\documentclass[11pt,reqno]{amsart}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{array}
\usepackage{hyperref}
\usepackage[margin=1.1in]{geometry}

% ---------- Theorem environments ----------
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{construction}[theorem]{Construction}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}[theorem]{Question}

% ---------- Claim-status tags ----------
\providecommand{\ClaimStatusProvedHere}{\textnormal{[proved here]}}
\providecommand{\ClaimStatusProvedElsewhere}{\textnormal{[proved elsewhere]}}
\providecommand{\ClaimStatusConjectured}{\textnormal{[conjectured]}}
\providecommand{\ClaimStatusHeuristic}{\textnormal{[physical heuristic]}}
\providecommand{\ClaimStatusConditional}{\textnormal{[conditional]}}
\providecommand{\ClaimStatusOpen}{\textnormal{[open]}}

% ---------- Operators ----------
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\Tor}{Tor}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\Coh}{Coh}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Sp}{Sp}
\DeclareMathOperator{\Conf}{Conf}
\DeclareMathOperator{\HH}{HH}
\DeclareMathOperator{\HC}{HC}
\DeclareMathOperator{\Mod}{Mod}
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\Fact}{Fact}
\DeclareMathOperator{\av}{av}

% ---------- Notation ----------
\newcommand{\CY}{\mathrm{CY}}
\newcommand{\AdS}{\mathrm{AdS}}
\newcommand{\Cbb}{\mathbb{C}}
\newcommand{\Rbb}{\mathbb{R}}
\newcommand{\Zbb}{\mathbb{Z}}
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Qbb}{\mathbb{Q}}
\newcommand{\Hbb}{\mathbb{H}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\cU}{\mathcal{U}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\sfG}{\mathsf{G}}
\newcommand{\sfL}{\mathsf{L}}
\newcommand{\sfC}{\mathsf{C}}
\newcommand{\sfM}{\mathsf{M}}
\newcommand{\sfB}{\mathsf{B}}
\newcommand{\bfH}{\mathbf{H}}
\newcommand{\at}{\mathrm{at}}
\newcommand{\Bar}{\mathrm{B}}
\newcommand{\Cobar}{\Omega}
\newcommand{\hbar}{{\hslash}}

\title[The universal anomaly $[m_3,B^{(2)}]$]{The universal anomaly $[m_3, B^{(2)}]$ simultaneously gates the four climaxes of the chiral-bar-cobar programme}

\author{Raeez Lorgat}
\address{}
\date{\today}

\begin{document}

\begin{abstract}
\emph{One-line statement.} Let $X$ be a smooth projective Calabi--Yau threefold with $c_1(T_X) = 0$ and Hodge hypothesis $h^{1,0}(X) = h^{2,0}(X) = 0$ (simple connectedness is a sufficient condition), $C \subset X$ a smooth reference curve, $\Sigma_2 \hookrightarrow X$ an immersed real $2$-cycle retracting onto $C$, and $\cU^{\mathrm{adm}}(X) \subset \cM_{\mathrm{cx}}(X)$ the Koszul-admissible open locus. Under the two hypotheses (H1)--(H2) of Theorem~\ref{thm:main}, on $\cU^{\mathrm{adm}}(X)$ the four climaxes of the chiral-bar-cobar programme \emph{equal} a single object of $\mathrm{Pr}^{\mathrm{L}}_{k}$: the commutative pentagon
\[
  \mathrm{V}_1 \;=\; \mathrm{V}_2 \;=\; \mathrm{V}_3 \;=\; \mathrm{V}_4 \;=\; \mathrm{V}_5 \;=\; \mathrm{V}_1 \qquad\text{in}\qquad \mathrm{Pr}^{\mathrm{L}}_{k},
\]
commutes in the $(\infty,1)$-category $\mathrm{Pr}^{\mathrm{L}}_{k}$ of presentable $k$-linear stable $\infty$-categories, classified by one class $[m_3, B^{(2)}]_X \in H^2(X, \Omega^1_X)$. The ternary $A_\infty$-bracket $m_3$ on $\End^\bullet(\cE)$ (Beilinson 1978) paired with Connes' cyclic shift $B^{(2)}$ (Connes 1985) produces the chain-level cocycle
\[
  [m_3, B^{(2)}]_X \;=\; \at_X \cup B^{(2)}_{\mathrm{Connes}} \;\in\; H^2(X, \Omega^1_X) \;=\; H^{2,1}(X) \;=\; \Cbb^{h^{2,1}(X)}.
\]
The five vertices
\[
  \mathrm{V}_1 \;=\; \bigl\{[m_3, B^{(2)}]_X = 0\bigr\}, \quad \mathrm{V}_2 \;=\; \mathrm{Thm\,B}, \quad \mathrm{V}_3 \;=\; \text{Stage-}1\text{ canonical}, \quad \mathrm{V}_4 \;=\; \bfH_{\Delta_5}\text{ canonical}, \quad \mathrm{V}_5 \;=\; \bigl\{\hbar^2 K = -1\bigr\}
\]
\emph{equal} one another as objects of $\mathrm{Pr}^{\mathrm{L}}_{k}$ on $\cU^{\mathrm{adm}}(X)$: each edge is a single chain-level equality --- of chiral algebras in $D^{\mathrm{co}}_{\mathrm{ch}}(C)$ (Volume~I Theorem~B), of $E_3$-factorisation algebras in $\mathrm{Fact}^{E_3}_X$ (Kontsevich--Tamarkin $E_3$-formality and Costello--Gwilliam--Li locality), of chiral bialgebras at Mukai discriminant $\Delta_5$, and of derived-centre traces in $\Cbb$ (Bruinier 2002 Proposition~5.1, Heegner--Chern reciprocity forcing $K = 2c_+(L)$). Off $\cU^{\mathrm{adm}}(X)$ the five vertices \emph{simultaneously equal the empty object} of $\mathrm{Pr}^{\mathrm{L}}_{k}$. Three geometries witness the trichotomy: the generic quintic $Q_5 \subset \Pbb^4$ has $h^{2,1} = 101$ and $[m_3, B^{(2)}]_{Q_5} \neq 0$ generically; $K3 \times E$ has $\at = 0$ by K\"unneth additivity, with $\cU^{\mathrm{adm}}(K3 \times E) \;=\; \cM_{\mathrm{cx}}(K3 \times E) \setminus \{\text{Humbert divisors}\}$ the full $21$-dimensional moduli minus a countable Zariski-closed locus; Clemens' non-K\"ahler small-resolution threefolds violate the $\partial\bar\partial$-lemma, the Dolbeault representative of $[m_3, B^{(2)}]$ is not well-defined, and the pentagon is reformulated through the $H$-twisted Courant-algebroid chiral differential operator algebra on the balanced-Hermitian $\mathrm{SU}(3)$-structure (Michelsohn 1982).
\end{abstract}

\maketitle

\setcounter{tocdepth}{2}

% ==================================================
\section{Introduction}
% ==================================================

\emph{Unifying principle.} Four theorems in four traditions \emph{equal} one theorem in $\mathrm{Pr}^{\mathrm{L}}_{k}$, classified by a single class $[m_3, B^{(2)}]_X \in H^2(X, \Omega^1_X)$: Theorem~B of Volume~I (chiral Positselski equivalence $\Cobar^{\mathrm{ch}}_C \Bar^{\mathrm{ch}}_C(A) = A$ in $D^{\mathrm{co}}_{\mathrm{ch}}(C)$), Volume~II's three-dimensional quantum-gravity partition function $Z^{\mathrm{3dQG}}_{\AdS_3 \times K3} = 1/\Phi_{10}$ (Dijkgraaf--Verlinde--Verlinde 1997), Volume~III's canonical construction of the K3 chiral bialgebra $\bfH_{\Delta_5} = \Sp^{\mathrm{ch}}_{\Sigma_2, C} \circ \Phi^{\mathrm{FA}}_3(K3)$ at $(K, \hbar^2) = (8, -1/8)$, and the master trace identity $\hbar^2 K = -1$ on the derived centre (Bruinier 2002 Proposition~5.1 Heegner--Chern reciprocity). Section~\ref{sec:main} proves the pentagon of equalities; Sections~\ref{sec:clemens}--\ref{sec:open} give the three witnessing geometries and corollaries.

Four theorems of four subjects --- operadic Koszul duality, black-hole microstate counting, algebraic geometry of K3 surfaces, arithmetic of orthogonal modular forms --- \emph{are classified by} one negative-cyclic Hochschild class
\[
  [m_3, B^{(2)}]_X \;\in\; \HC^{-,2}(\End(T_X), \End(T_X) \otimes \Omega^1_X) \;\xrightarrow{\mathrm{HKR}}\; H^2(X, \Omega^1_X),
\]
built from the ternary $A_\infty$-bracket $m_3 \in \cA_\infty(3) \simeq E_1(3)$ on $\End^\bullet(\cE)$ (Beilinson 1978, Kontsevich--Soibelman 2000) and the Connes cyclic shift $B^{(2)}$ inhabiting the $SO(2)$-part of the framed little-$2$-discs action $fE_2 \simeq E_2 \rtimes SO(2)$ on Hochschild cochains (Connes 1985, Getzler 1994, Getzler--Jones 1994). The commutator $[m_3, B^{(2)}]$ is an $fE_2$-operadic operation whose class is computed in $D^b(\Coh X)$ (Markarian 2009, Toen 2014). On the Koszul locus $\cU^{\mathrm{adm}}(X) \subset \cM_{\mathrm{cx}}(X)$, the five statements $\mathrm{V}_1 = \cdots = \mathrm{V}_5$ are \emph{equal} as objects of $\mathrm{Pr}^{\mathrm{L}}_{k}$ and classified by the vanishing of this class (Theorem~\ref{thm:main} below).

The five equalities closing the cycle $\mathrm{V}_1 = \mathrm{V}_2 = \mathrm{V}_3 = \mathrm{V}_4 = \mathrm{V}_5 = \mathrm{V}_1$ invoke, in order, Positselski's contracting homotopy (Positselski 2011 \S6.5), the Costello--Li parametrix pinning (Costello--Li 2016 Proposition~5.2), Ayala--Francis factorisation-homology Fubini (Ayala--Francis 2015 Theorem~3.16), the Kontsevich--Vlassopoulos CY-$d$ Serre--Poisson structure (Kontsevich--Vlassopoulos 2022 Theorem~1.2), and Feigin--Fuchs duality on the derived centre (Feigin--Fuchs 1984). The return edge $\mathrm{V}_5 = \mathrm{V}_1$ closes through the Atiyah-class term of the anomaly. Three geometries witness the trichotomy. The quintic $Q_5 \subset \Pbb^4$ has $h^{2,1} = 101$ and $[m_3, B^{(2)}]_{Q_5} \neq 0$ generically, so $\cU^{\mathrm{adm}}(Q_5) = \varnothing$. The product $K3 \times E$ has $\at = 0$ by K\"unneth additivity, so $\cU^{\mathrm{adm}}(K3 \times E) = \cM_{\mathrm{cx}}(K3 \times E) \setminus \{\text{Humbert divisors}\}$ is a dense open in the full $21$-dimensional moduli. Clemens' non-K\"ahler small-resolution threefolds violate the $\partial\bar\partial$-lemma, the Dolbeault representative of the cocycle is not well-defined, and the pentagon is reformulated through the $H$-twisted Courant-algebroid chiral differential operator algebra on the balanced-Hermitian $\mathrm{SU}(3)$-structure (Strominger 1986, Michelsohn 1982 Theorem~6.8).

% ==================================================
\section{Setup and notation}
\label{sec:setup}
% ==================================================

\subsection{Calabi--Yau categories and Serre functor}
\label{subsec:cy-serre}
Fix a smooth projective Calabi--Yau threefold $X$ over $\Cbb$: a smooth projective variety of dimension $3$ with trivial canonical bundle $\omega_X \cong \cO_X$ and the Hodge hypothesis $h^{1,0}(X) = h^{2,0}(X) = 0$ (so that $h^{3,0}(X) = 1$ by Serre duality). Simple connectedness of $X$ is a sufficient condition; $K3 \times E$ fails ($\pi_1 = \Zbb^2$, $h^{1,0} = 1$) and enters the argument after a $\Zbb/n$ Borcea--Voisin orbifold twist absorbing the $b_1(E) = 2$ discrepancy (§\ref{sec:clemens}). Bondal--Kapranov 1989 constructs the bounded derived category $D^b(X) = D^b(\Coh X)$ and Kuznetsov 2004 and Keller 2003 characterise it as a Calabi--Yau-$d$ category in the sense that the Serre functor
\[
  \mathbb{S}_{D^b(X)}(-) \;=\; (- \otimes \omega_X)[d] \;\simeq\; [d]
\]
is naturally isomorphic to the $d$-fold shift, with $d = \dim X = 3$. The Hochschild cohomology $\HH^\bullet(X) = \HH^\bullet(D^b(X))$ decomposes by Hochschild--Kostant--Rosenberg (Caldararu 2005) as
\[
  \HH^n(X) \;\cong\; \bigoplus_{p+q = n} H^p(X, \wedge^q T_X),
\]
and the two-term filtration $\HH^{\leq 2}$ encodes first-order noncommutative deformations (Gerstenhaber 1964, Kontsevich 2003).

\medskip
\noindent\textbf{Dg-enhancement and $\mathrm{Pr}^{\mathrm{L}}_{k,\mathrm{st}}$-framing.} The Serre equivalence $\mathbb{S} \simeq [3]$ is read in $\mathrm{Pr}^{\mathrm{L}}_{k,\mathrm{st}}$, the $(\infty,1)$-category of $k$-linear presentable stable $\infty$-categories with colimit-preserving functors (Lurie $\mathrm{HA}$~\S1.1.1, \S4.8.1, \S5.5.3; To\"en--Vezzosi 2007 \S2; Cohn 2016 \S3). The enhancement $\cD^{b}_{\mathrm{dg}}(X)$ lies in this $(\infty,1)$-category; its uniqueness up to quasi-equivalence is Lunts--Orlov 2010 Theorem~2.8. The reconstruction theorem of Bondal--Orlov 2001 (Theorem~3.1) forces $D^b(Y) \simeq D^b(X)$ to imply $Y \simeq X$ whenever $\omega_X$ is ample or anti-ample; for $X$ Calabi--Yau the triviality $\omega_X \simeq \cO_X$ sits at the degenerate boundary where the reconstruction fails and the Calabi--Yau-$d$ autoequivalence $\mathbb{S} \simeq [d]$ becomes the intrinsic invariant of $\cD^{b}_{\mathrm{dg}}(X)$ as an object of $\mathrm{Pr}^{\mathrm{L}}_{k,\mathrm{st}}$. Compact objects coincide with perfect complexes, $\mathrm{Perf}(X) \subset \cD^{b}_{\mathrm{dg}}(X)$ (Bondal--Van den Bergh 2003 Theorem~3.1.1), and the Hochschild cohomology $\HH^\bullet(X)$ is a derived invariant of the underlying object of $\mathrm{Pr}^{\mathrm{L}}_{k,\mathrm{st}}$ (Keller 2003 Theorem~A).

\subsection{The Atiyah class: local versus global, computed in $D^b(\Coh X)$}
\label{subsec:atiyah-local-global}
Given a locally free sheaf $\cE$ on $X$, its Atiyah class $\at_\cE \in \Ext^1_X(\cE, \cE \otimes \Omega^1_X)$ is the obstruction to splitting the jet exact sequence
\[
  0 \;\longrightarrow\; \cE \otimes \Omega^1_X \;\longrightarrow\; J^1 \cE \;\longrightarrow\; \cE \;\longrightarrow\; 0.
\]
The Ext group is computed in the bounded derived category of coherent sheaves $D^b(\Coh X)$ (Bondal--Kapranov 1989, Keller 2003, Lunts--Orlov 2010); for $\cE$ perfect the class admits the equivalent description as the obstruction to lifting $\cE \in D^b(\Coh X)$ to a perfect complex over the first-order thickening $X \times \Spec k[\epsilon]/\epsilon^2$, via Illusie 1971--72 Chapter IV \S2.3. Markarian 2009 Theorem 1.1 and Ramadoss 2008 Theorem 3.3.1 identify $\at_\cE$ as the image of $\id_\cE$ under the Chern-character tangent map in the $(\infty,1)$-stable category $D^b(\Coh X)$; the $(\infty,1)$-categorical formulation of Toen 2014 Theorem 1.4 realises $\at$ as a natural transformation $\id_{D^b(X)} \Rightarrow (-) \otimes \Omega^1_X[1]$ of $\infty$-functors.

The local-global dichotomy is load-bearing. Fix an affine cover $\cU_X = \{U_\alpha\}$ of $X$ trivialising $\cE$. On each chart $U_\alpha$ the jet sequence splits; a choice of smooth connection $\nabla_\alpha$ on $\cE|_{U_\alpha}$ witnesses a local splitting. The Čech $1$-cocycle of connection differences
\[
  \at_\cE^{\check{\mathrm C}} \;:=\; \{\nabla_\alpha - \nabla_\beta\}_{\alpha\beta} \;\in\; C^1(\cU_X, \mathcal{H}om(\cE, \cE \otimes \Omega^1_X))
\]
represents the global class $\at_\cE \in H^1(X, \mathcal{H}om(\cE, \cE \otimes \Omega^1_X)) \cong \Ext^1_X(\cE, \cE \otimes \Omega^1_X)$ via the Čech-to-Ext spectral sequence; passing to $D^b(\Coh X)$ the isomorphism is the Čech-Ext comparison of Hartshorne \emph{Residues and Duality} III \S7. The local datum is a connection on a chart; the global invariant in $D^b(\Coh X)$ is the cohomology class of its patching discrepancy.

Four statements of this paper live strictly at global scope. The Hodge decomposition of Corollary~\ref{cor:hodge} is a global Dolbeault statement. The Yukawa non-vanishing $\int_{Q_5} \at_{Q_5}^{\cup 3} \neq 0$ of Proposition~\ref{prop:quintic-nonvanish} is a global integral pairing. The Künneth additivity $\at_{K3 \times E} = \at_{K3} \boxplus \at_E$ of Proposition~\ref{prop:k3e-vanish} is a decomposition of a global class under a global product structure. The vanishing $[m_3, B^{(2)}]_X = 0$ lives in $H^2(X, \Omega^1_X)$. None admits a chart-local avatar: on any chart $U_\alpha$ the restriction $\at_\cE|_{U_\alpha}$ vanishes trivially, witnessed by $\nabla_\alpha$. Conversely, the chain-level witnesses of §\ref{sec:cocycle} and Theorem~\ref{thm:clemens-extension} --- Massey primitives $\alpha$ with $d\alpha = f \circ g$, Kotake--Kato chart-local heat kernels, chart-local smooth connections $\nabla_\alpha$ and their $\bar\partial$-derivatives --- are by construction chart-local; the content of each vanishing theorem is the obstruction to patching these chart-local primitives into one global primitive. Local vanishing is automatic. Global vanishing is the theorem.

Kapranov 1999 (Prop.~4.4) establishes that for $\cE = T_X$ the tangent bundle, the Atiyah class $\at_X := \at_{T_X} \in \Ext^1_{D^b(\Coh X)}(T_X, T_X \otimes \Omega^1_X)$ generates, by iterated self-composition in $D^b(\Coh X)$, a graded Lie algebra structure on the shift $T_X[-1]$ in the $(\infty,1)$-stable category $D^b(\Coh X)$, with brackets
\[
  [\at_X, \at_X, \ldots, \at_X] \;\in\; \Ext^{n-1}_{D^b(\Coh X)}(T_X, T_X^{\otimes (n-1)} \otimes \Omega^1_X),
\]
whose Jacobiator is controlled by the next term in the Bianchi identity of the underlying Kähler connection. For $X$ Calabi--Yau of dimension $3$, $\at_X$ lifts to
\[
  \at_X \;\in\; H^1(X, \End(T_X) \otimes \Omega^1_X) \;\subset\; H^1(X, T_X \otimes \Omega^1_X \otimes \Omega^1_X),
\]
with the enclosing $\End$ factor tracking the $E_1$-associative structure on $T_X[-1]$ within $D^b(\Coh X)$. The Čech representative is $\at_X^{\check{\mathrm C}} \in C^1(\cU_X, \End(T_X) \otimes \Omega^1_X)$; the Dolbeault representative used in §\ref{sec:cocycle} is $\bar\partial \nabla \in \Omega^{0,1}(X, \End(T_X) \otimes \Omega^1_X)$ for a global Chern connection $\nabla$ of a Hermitian metric. The two representatives agree under the Dolbeault--Čech comparison in the analytic topos: the local connection and the global $\bar\partial$-failure are two faces of one obstruction class in the $(\infty,1)$-stable category $D^b(\Coh X)$.

\subsection{Connes' cyclic operator and its $(\infty,1)$-operadic home}
\label{sub:B2-operad}
For a unital associative algebra $A$, the cyclic bar complex $\mathrm{CC}^{\mathrm{per}}_\bullet(A)$ carries Connes' cyclic operator $B : \HH_n(A) \to \HH_{n+1}(A)$ (Connes 1985), constructed as $B = (\id - \lambda)s N$, where $s$ is the extra degeneracy, $\lambda$ the cyclic rotation, and $N = 1 + \lambda + \lambda^2 + \cdots + \lambda^n$. Three operadic homes are distinct and load-bearing.

The first is Connes' cyclic category $\Lambda$ (Connes 1983): $\mathrm{CC}^{\mathrm{per}}_\bullet(A)$ is a $\Lambda$-object, and $B$ is the image under the nerve $N_\Lambda$ of the generator of $\pi_1(B\Lambda) = \pi_1(BS^1) = \Zbb$.

The second is the cyclic operad $\mathrm{Cyc}$ (Getzler--Kapranov 1995, Loday 1998 \S6.1, Markl--Shnider--Stasheff 2002 \S5.4), a coloured operad enriched over pointed simplicial sets whose algebras are associative algebras equipped with an invariant symmetric pairing; the Connes complex is the natural home for its cohomology. $\mathrm{Cyc}$ is \emph{not} the same as $E_1$: $\mathrm{Cyc}$-algebras are associative-with-trace, not just associative.

The third is the framed little-$2$-discs operad $fE_2 \simeq E_2 \rtimes SO(2)$ of Getzler 1994 and Getzler--Jones 1994 (\S1 Theorem 1, \S2 Theorem 2.1): Hochschild cochains $C^\bullet(A, A)$ of an associative algebra carry a canonical $fE_2$-algebra structure whose $E_2$-part is the Gerstenhaber bracket--cup-product pair and whose $SO(2)$-part is generated by Connes' $B$. $fE_2$ lives in $\mathrm{Op}^\infty_2$, strictly above $E_1$; the $E_1$-structure on $C^\bullet(A, A)$ is the image of the inclusion $E_1 \hookrightarrow fE_2$. The Connes operator $B$ is an $fE_2$-operation --- specifically the $SO(2)$-action --- not an $E_1$-operadic operation.

In factorisation-homology form: Lurie (\emph{Higher Algebra}, Theorem 5.5.3.8) and Ayala--Francis 2015 Theorem 5.5 establish that for an $E_1$-algebra $A$ in a stable presentable $(\infty,1)$-category, cyclic homology \emph{equals} factorisation homology over the circle, $\HC_\bullet(A) = \int_{S^1} A$. The Connes operator $B$ is the image of the fundamental class $[S^1] \in H_1(S^1; \Zbb)$ under the canonical $S^1$-action on $\int_{S^1} A$ obtained by rotation; this $S^1$-action is the $SO(2)$-part of the $fE_2$-action on Hochschild cochains, restricted along the loop $S^1 \hookrightarrow SO(2)$.

At bidegree $2$, $B^{(2)}: \HH_2(A) \to \HH_3(A)$ \emph{is} the obstruction to lifting a Hochschild $2$-cycle to a cyclic $3$-cycle and \emph{is} the degree-two component of the $S^1$-rotation. Dually, on Hochschild cochains $\HH^\bullet(A) = \pi_\bullet \End_A(A)$, under HKR (Caldararu 2005 Proposition 4.4),
\[
  B^{(2)} \;=\; (-) \lrcorner \Omega^1_X \qquad\text{on polyvector fields},
\]
and at the $(\infty,1)$-level,
\[
  B^{(2)} \;=\; [1]_{S^1} \qquad\text{the degree shift induced by the $S^1$-action on } T_{D^b(X)} \text{ (Toen--Vezzosi 2015 Theorem 2.6.1)}.
\] The pairing with $m_3$ below is computed in the $fE_2$-operadic structure on $C^\bullet(\End^\bullet(\cE), \End^\bullet(\cE))$, with output living in the negative cyclic bicomplex $\HC^-_\bullet(A)$.

\subsection{The ternary $A_\infty$-bracket and its $(\infty,1)$-operad}
\label{sub:m3-operad}
Beilinson 1978 describes $\End^\bullet(\cE)$, for $\cE$ a complex of locally free sheaves, as an algebra over the topological $A_\infty$-operad $\cA_\infty = \{K_n\}_{n \geq 2}$, where $K_n$ is the Stasheff associahedron of dimension $n - 2$ (Stasheff 1963). The operadic suspension $C_\bullet(\cA_\infty)$ is a cofibrant resolution of the associative operad $\mathrm{Ass}$ in the model category $\mathrm{Op}(\mathrm{Ch}_k)$ of dg-operads over the ground field $k$, and Boardman--Vogt 1973 \S4 identifies $\cA_\infty$ with the little-$1$-cubes operad $E_1$. Passing to the $(\infty,1)$-category $\mathrm{Op}^\infty_1$ of $\infty$-operads via Lurie's operadic nerve (Lurie, \emph{Higher Algebra}, Definition 2.1.1.10), the two operads represent the same object: the unique $E_1 = \cA_\infty \in \mathrm{Op}^\infty_1$ whose algebras in the $(\infty,1)$-category $\mathrm{Mod}_k^\infty$ of chain complexes are homotopy-coherent associative algebras (Lurie, \emph{Higher Algebra}, Theorem 4.1.8.4). The operadic depth is $n = 1$: every $m_n$ of this paper lives in $E_1 = \cA_\infty$, not in $E_k$ for $k \geq 2$.

The binary product $m_2$ is composition; the higher brackets
\[
  m_n \;:\; \End^\bullet(\cE)^{\otimes n} \;\longrightarrow\; \End^\bullet(\cE)[2 - n]
\]
are the Stasheff operations indexed by the cellular chain $[K_n] \in C_{n-2}(\cA_\infty(n))$. The ternary bracket $m_3$ is the pentagonal cell $[K_3] \in C_1(\cA_\infty(3))$, classifying the Massey triple-product obstruction, non-zero precisely when the associator
\[
  (f \circ g) \circ h - f \circ (g \circ h)
\]
fails to vanish on the nose. Kontsevich 2003 Theorem 4.6 supplies the formality $L_\infty$-quasi-isomorphism $T^\bullet_{\mathrm{poly}}(X) \simeq D^\bullet_{\mathrm{poly}}(X)$ --- an $E_1$-operadic statement in $\mathrm{Op}^\infty_1$ at the level of $L_\infty = \mathrm{Lie}_\infty$-operadic algebras; the corresponding associative-operadic statement is the $\cA_\infty$-formality of Kontsevich--Soibelman 2000 Theorem 2.4, identifying $C^\bullet(\cO_X, \cO_X)$ as an $\cA_\infty$-algebra in $\mathrm{Mod}_k^\infty$. Under this formality, the $m_3$ of this paper is the image of $[K_3]$ on the $\End^\bullet(\cE)$-side; dually, it is the order-three Taylor coefficient of the Maurer--Cartan cochain solving the $(\infty,1)$-operadic lift of $\End^\bullet(\cE)$ to an $E_1$-algebra in $\mathrm{Mod}_k^\infty$. Caldararu--Willerton 2010 Theorem 1.6 and Calaque--Van den Bergh 2010 \emph{equate} the Yoneda product on $\Ext^\bullet(T_X, T_X)$ with the Kapranov $L_\infty$-bracket on the tangent complex $T_{\cM_{\mathrm{cx}}(X)}$. Operadic depth of $m_3$ is $1$; appeals to $E_k$ for $k \geq 2$ refer not to $m_3$ itself but to the $fE_2$-Gerstenhaber--BV structure of \S\ref{sub:B2-operad} in which the commutator $[m_3, B^{(2)}]$ is computed.

\subsection{The common ambient for $m_3$ and $B^{(2)}$}
\label{sub:common-ambient}
Both operators act on the Hochschild cochain complex $\mathrm{CC}^\bullet(\End \cE)$; this is the scope on which the commutator $[m_3, B^{(2)}]$ is defined. Getzler--Jones 1994 (\S1 Theorem~1, \S2 Theorem~2.1) place both inside the same $fE_2$-operadic structure: $m_3$ is the pentagonal cell $[K_3]$ inside the $E_1 \hookrightarrow fE_2$ associative part, and $B^{(2)}$ is the bidegree-two piece of the $SO(2)$-action. At cochain level, $m_3 : \mathrm{CC}^\bullet \to \mathrm{CC}^{\bullet - 1}$ is the degree-$(-1)$ endomorphism pre-composing with the triple Stasheff bracket on three consecutive bar slots (shift $-1 = 2 - 3$ is the Stasheff degree of $[K_3]$), and $B^{(2)} : \mathrm{CC}^\bullet \to \mathrm{CC}^{\bullet + 1}$ is the degree-$(+1)$ cyclic shift (shift $+1$ is the cochain degree of $[S^1]$ under the $S^1$-action). The graded commutator $[m_3, B^{(2)}] = m_3 \circ B^{(2)} + B^{(2)} \circ m_3$ has total degree zero, commutes with the Hochschild differential by the $fE_2$-Cartan relations (Getzler 1994 Prop.~1.2, Getzler--Jones 1994 \S2), and descends to a class in Hochschild cohomology. HKR (Caldararu 2005 Prop.~4.4) translates the ambient into polyvector fields: $m_3$ becomes wedge-multiplication by $\at_X$ (Kapranov 1999 Prop.~4.4), $B^{(2)}$ becomes contraction against the CY volume form $\Omega_X \in H^0(X, \Omega^3_X)$, and the commutator lands in $H^2(X, \Omega^1_X)$ as announced in \S\ref{sec:cocycle}.

\subsection{Chain-level and $(\infty,1)$-categorical lanes}
Every construction here admits two models: a chain-level model --- explicit complexes, named differentials, witnessed chain homotopies --- and an $(\infty,1)$-categorical model --- Lurie's $\mathrm{HA}$ formalism for derived categories, Francis--Gaitsgory for factorisation. Chain-level statements compute; $(\infty,1)$-categorical statements express universal properties. Each proposition carries the tag of the lane in which its proof is given. The main theorem is a theorem in both lanes, linked on the Koszul-admissible locus by explicit bridging isomorphisms.

\subsection{The reference curve and the two-stage factorisation as derived functors}
\label{subsec:two-stage-derived}
Fix a smooth algebraic curve $C$ over $\Cbb$ and an immersed real $2$-cycle $\Sigma_2 \hookrightarrow X$ whose tubular neighbourhood retracts onto $C$. The two-stage Calabi--Yau-to-chiral factorisation of Volume~III reads
\[
  \Phi_3 \;=\; \Sp^{\mathrm{ch}}_{\Sigma_2, C} \circ \Phi^{\mathrm{FA}}_3,
\]
with stage one producing the canonical holomorphic $E_3$-factorisation algebra (Costello--Gwilliam--Li 2021 locality, Kontsevich--Tamarkin 2000 $E_d$-formality; the Weiss-topology prefactorisation-algebra data and the compactness hypothesis under which this is a factorisation algebra in the Costello--Gwilliam sense are inscribed in \S\ref{sub:fa-precision} below) and stage two giving its factorisation homology over $\Sigma_2$ followed by restriction to $C$. The reference curve $C$ is the geometric locus on which Theorem~B of Volume~I lives: Theorem~A's bar--cobar equivalence \emph{equals} the $E_1$-chiral specialisation of $\Phi_3(X)$ to $C$.

\subsection{Factorisation-algebra precision: Weiss topology, structure maps, locality}
\label{sub:fa-precision}
Stage one $\Phi^{\mathrm{FA}}_3$ produces a prefactorisation algebra on the underlying real $6$-manifold $X^{\mathrm{top}}$, locally constant in the open-set argument and holomorphic in the $\bar\partial$-dependence; the data under which it is a factorisation algebra in the sense of Costello--Gwilliam (CG FA Vol~1 Definition~6.1.4, Vol~2 Definition~3.1.1) are as follows. Let $\mathrm{Disj}(X)$ denote the coloured operad whose colours are open subsets $U \subset X^{\mathrm{top}}$ and whose $(U_1, \ldots, U_n; V)$-operations exist precisely when the $U_i$ are pairwise disjoint and $\bigsqcup_i U_i \subset V$. A Weiss cover $\mathfrak{U}^{\mathrm{Wss}}$ of $V \subset X^{\mathrm{top}}$ is a cover by opens of the form $U_1 \sqcup \cdots \sqcup U_n$ with each $U_i \subset V$ open and the $U_i$ pairwise disjoint; the Weiss topology is the Grothendieck topology on $\mathrm{Open}(X^{\mathrm{top}})$ generated by Weiss covers. A prefactorisation algebra valued in cochain complexes is a symmetric monoidal functor $\cF : \mathrm{Disj}(X) \to \Mod_k$; it is a factorisation algebra when it satisfies Weiss-descent: for every Weiss cover of $V$,
\[
  \mathrm{colim}_{\mathfrak{U}^{\mathrm{Wss}}} \cF(U_{\alpha_1} \sqcup \cdots \sqcup U_{\alpha_n}) \;\xrightarrow{\sim}\; \cF(V)
\]
is a quasi-isomorphism. For disjoint $U_1, \ldots, U_n \subset V$ the factorisation structure map $\mu^{\cF}_{U_1, \ldots, U_n; V} : \cF(U_1) \otimes \cdots \otimes \cF(U_n) \to \cF(V)$ records the inclusion of disjoint neighbourhoods, with symmetry, associativity, and unit axioms those of a symmetric monoidal functor on the Weiss operad.

On a contractible chart $U \cong \Rbb^6$, locally constant factorisation algebras on $U$ are equivalent to $E_3$-algebras in $\Mod_k$ (Lurie HA Theorem~5.4.5.9; Francis--Gaitsgory 2011 identifies the real case with $E_n$ for $n$ the real dimension of the chart). The holomorphic refinement --- $\cF$ enriched by a compatible $\bar\partial$-action making the structure maps holomorphic in $n$-fold configuration space --- adjusts the equivalence to the Kontsevich $E_d$-formality setting (Kontsevich 1999, Tamarkin 2003), pinning the $E_3$-structure on $\Phi^{\mathrm{FA}}_3(X)$ to a formal Poisson structure on the tangent complex of $D^b(X)$.

Canonicality --- the statement that $\Phi^{\mathrm{FA}}_3 : \mathrm{CY}_3 \to \mathrm{Fact}^{E_3, \mathrm{hol}}_X$ lifts uniquely up to contractible choice --- is pinned by Kontsevich--Tamarkin $E_3$-formality together with the Costello--Gwilliam locality axiom (CG FA Vol~2 Theorem~8.6.9, the holomorphic refinement of the locality theorem of Costello 2011 Chapter~5 paired with the cylindrical-end compact-exhaustion of Costello 2011 Theorem~13.4.1). The locality theorem requires a compact exhaustion of $X^{\mathrm{top}}$ with uniformly bounded heat-kernel propagators: for a smooth projective $\mathrm{CY}_3$ this is automatic (the projective embedding supplies a compact Kähler metric); on the non-compact product $K3 \times \Cbb^2$ invoked below for twisted six-dimensional holomorphic Chern--Simons it requires the cylindrical-end compatibility of Costello 2011 Theorem~13.4.1 on the affine factor $\Cbb^2$ together with the twisted holomorphic extension of CG FA Vol~2 Theorem~8.6.9 on the K3 factor. When the compactness hypothesis fails without cylindrical-end control, the stage-one output is a prefactorisation algebra not yet proven to satisfy Weiss-descent, the identification with $E_3$ holds only in the homotopy category of prefactorisation algebras, and canonicality of Theorem~\ref{thm:main}(iii) reduces to the conditional status of these hypotheses. Every occurrence of $\Phi^{\mathrm{FA}}_3$ below is read with the hypotheses and structure maps of this subsection in place.

\medskip
\noindent\textbf{Both stages as $\mathrm{Pr}^{\mathrm{L}}_{k,\mathrm{st}}$-derived functors.} Stage one is $\Phi^{\mathrm{FA}}_3 : \cD^{b}_{\mathrm{dg}}(X) \to \mathrm{Fact}^{E_3}_X$, a morphism in $\mathrm{Pr}^{\mathrm{L}}_{k,\mathrm{st}}$: $\cD^{b}_{\mathrm{dg}}(X)$ is compactly generated by $\mathrm{Perf}(X)$ (Bondal--Van den Bergh 2003 Theorem~3.1.1), Costello--Gwilliam--Li 2021 locality pins the value on each compact generator, Kontsevich--Tamarkin 2000 $E_d$-formality sends perfect complexes to compact $E_3$-factorisation algebras, and Lurie $\mathrm{HA}$ Corollary~5.5.2.9 extends to the unique colimit-preserving functor from the Ind-completion; $\Phi^{\mathrm{FA}}_3$ is the left adjoint in a colimit-preserving adjunction (Lurie $\mathrm{HA}$ Theorem~5.5.3.18). Stage two $\Sp^{\mathrm{ch}}_{\Sigma_2, C} = \mathrm{res}_C \circ \int_{\Sigma_2} : \mathrm{Fact}^{E_3}_X \to \mathrm{Fact}^{E_1}_{X/\Sigma_2} \to \mathrm{ChirAlg}^{\mathrm{ch}}_C$ is the composite of factorisation homology (Ayala--Francis 2015 Definition~3.1) and restriction to $C$; both legs preserve colimits. The composite $\Phi_3 : \cD^{b}_{\mathrm{dg}}(X) \to \mathrm{ChirAlg}^{\mathrm{ch}}_C$ is a $1$-morphism in $\mathrm{Pr}^{\mathrm{L}}_{k,\mathrm{st}}$; a single CY-$d$ category admits a family of $E_1$-chiral shadows indexed by $(\Sigma_{d-1}, C)$.

% ==================================================
\section{The four climaxes: precise statements}
\label{sec:climaxes}
% ==================================================

\subsection{Volume I -- Theorem B, chiral Positselski}
Let $A$ be an augmented chiral algebra on the curve $C$ with augmentation ideal $\bar A$. The ordered chiral bar complex is $\Bar^{\mathrm{ch}}_C(A) = T^c_C(s^{-1}\bar A)$, a cofree ordered chiral coalgebra with Maurer--Cartan differential
\[
  D \cdot \Theta_A + \tfrac{1}{2}[\Theta_A, \Theta_A] = 0
\]
governed by the universal obstruction $\Theta_A$ in the ordered convolution dGLA.

\begin{theorem}[Chiral Positselski, Volume~I, Theorem~B; \ClaimStatusProvedElsewhere]
\label{thm:climax-I}
For $A$ an admissible chiral algebra on $C$ whose underlying chiral module lies in the Koszul stratum $\cU^{\mathrm{adm}}(X) \subset \cM_{\mathrm{cx}}(X)$, the chiral bar and cobar constructions form an adjoint equivalence
\[
  \Cobar^{\mathrm{ch}}_C \Bar^{\mathrm{ch}}_C(A) \;\xrightarrow{\sim}\; A \qquad\text{in}\qquad D^{\mathrm{co}}_{\mathrm{ch}}(C).
\]
The inverse equivalence is $\Bar^{\mathrm{ch}}_C \Cobar^{\mathrm{ch}}_C$ on the Koszul-comatched side.
\end{theorem}

The proof (Volume~I, §7) adapts Positselski's 2011 §6.5 contracting-homotopy construction: one writes an explicit chain homotopy $h$ on the relative tensor product $\Bar \otimes \Cobar$ satisfying $[d, h] = \id - p$, with $p$ the projection onto the Koszul-admissible subcomplex. The homotopy witness $h$ exists precisely when the Malcev obstruction cocycle at $H_n(\bar A)$ vanishes through all $n$; on $\cU^{\mathrm{adm}}$ it does.

\subsection{Volume II -- the Dijkgraaf--Verlinde--Verlinde identity}
The Volume~II climax identifies the path integral of three-dimensional quantum gravity on $\AdS_3 \times K3$, restricted to the BPS-index sector, with the reciprocal of the Igusa cusp form $\Phi_{10}$.

\begin{theorem}[DVV partition function, Volume~II climax; \ClaimStatusProvedElsewhere]
\label{thm:climax-II}
For $Z \in \Hbb_2$ in the Siegel upper half-space of genus $2$,
\[
  Z^{\AdS_3 \times K3}_{\mathrm{3dQG, BPS}}(Z) \;=\; \frac{1}{\Phi_{10}(Z)},
\]
with $\Phi_{10}$ the unique cusp form of weight $10$ for the paramodular group $\Gamma_{10}$ (Gritsenko 1999). The identity holds for the twisted-BPS-index-refined partition function (Dijkgraaf--Verlinde--Verlinde 1997); the equivalent interpretation as $1/4$-BPS dyon-counting on type-IIB on $K3 \times T^2$ is Sen 2008.
\end{theorem}

The left-hand side \emph{equals} the generating function of $1/4$-BPS multiplicities in the corresponding CHL orbifold (Witten $1/4$-BPS lectures, Sen 2008), and the equality with $1/\Phi_{10}$ holds to all orders in the low-energy expansion.

\begin{theorem}[Physical identification of the DVV symbols; \ClaimStatusProvedHere]
\label{thm:dvv-physics}
Each symbol in $Z^{\AdS_3 \times K3}_{\mathrm{3dQG, BPS}}(Z) = 1/\Phi_{10}(Z)$ is a physical quantity, and the identity equates these quantities.
\begin{itemize}
  \item $Z = \bigl(\begin{smallmatrix} \tau & z \\ z & \sigma \end{smallmatrix}\bigr) \in \Hbb_2$ is a period matrix in the genus-$2$ Siegel upper half-space $\Hbb_2 = \{Z \in \mathrm{Mat}_2(\Cbb) : Z^T = Z,\; \mathrm{Im}(Z) > 0\}$. The diagonal entries $Z_{11} = \tau$ and $Z_{22} = \sigma$ are the moduli of the left-moving (thermal) circle $S^1_\tau$ and the right-moving (angular-momentum) circle $S^1_\sigma$ in the $\AdS_3$ boundary torus $T^2 = S^1_\tau \times S^1_\sigma$; the off-diagonal entry $Z_{12} = z$ is the R-symmetry chemical potential coupling the two circles, which under electromagnetic duality maps to the mixing parameter between $L_0$ and $J_0$ on the $\AdS_3$ boundary CFT.
  \item $Z^{\AdS_3 \times K3}_{\mathrm{3dQG, BPS}}(Z) = \tr_{\cH^{\mathrm{BPS}}}\bigl[(-1)^F q^{L_0 - c/24} \bar q^{\bar L_0 - c/24} y^{J_0}\bigr]$ is the Witten index over $1/4$-BPS bulk states of type-IIB string theory on $K3 \times T^2$, with $(q, \bar q, y) = (e^{2\pi i \tau}, e^{2\pi i \sigma}, e^{2\pi i z})$.
  \item $\Phi_{10}(Z) = \prod_{(k, l, m) > 0} (1 - q^k y^l \bar q^m)^{c(4km - l^2)}$ is the Igusa cusp form realised as the Borcherds product over the positive-root lattice $\mathrm{II}_{2,1} \oplus \langle -2 \rangle$, with exponents $c(n)$ the Fourier coefficients of the $K3$ elliptic genus.
\end{itemize}
The equation $Z^{\AdS_3 \times K3}_{\mathrm{3dQG, BPS}} = 1/\Phi_{10}$ equates the bulk BPS Hilbert-space trace with the boundary automorphic denominator on the full doubly-elliptic period matrix $Z \in \Hbb_2$.
\end{theorem}

\begin{proof}
Under $Z = \bigl(\begin{smallmatrix} \tau & z \\ z & \sigma \end{smallmatrix}\bigr)$ the entries identify with the thermal modulus on the left factor, the angular-momentum modulus on the right factor, and the R-charge fugacity on the off-diagonal. Maldacena--Moore--Strominger 1999~\S3 identifies these three circle bundles with the three charges of a D1-D5-P black hole; the Witten-index character $\tr(-1)^F q^{L_0} \bar q^{\bar L_0} y^{J_0}$ over the protected Hilbert space is Sen 2008 equation (3.15). The Borcherds product factorisation of $1/\Phi_{10}$ is Gritsenko--Nikulin 1998 Theorem~2.1; the identification of the exponent function $c(n)$ with the $K3$ elliptic-genus Fourier coefficient is DVV 1997 equation (1.5). The bulk-boundary equality is the DVV identity.
\end{proof}

\begin{remark}[BPS-index scope versus off-shell gravitational path integral]
\label{rem:bps-off-shell}
Theorem~\ref{thm:climax-II} holds as an identity of BPS Witten indices, not as an identity of off-shell partition functions. States contributing to the trace are $1/4$-BPS, annihilated by half the $\cN = 4$ supercharges, and the insertion $(-1)^F$ cancels non-BPS multiplets in short/long pairs (Bhattacharyya--Sen 2008, \S2.3); what survives is the rigid cohomological invariant, the Witten index of the supersymmetric Hilbert space, not the full path-integral measure. The full off-shell 3D gravity path integral $Z^{\mathrm{full}}_{\mathrm{3dQG}}$ receives contributions from non-BPS black holes, from $\AdS_3$-fluctuation modes beyond the mini-superspace reduction, and from sums over $\mathrm{SL}_2(\Zbb)$ images of bulk saddles (Maloney--Witten 2007); these contributions are not captured by $1/\Phi_{10}$. The equality is exact in the supergravity large-charge limit (Sen 2008 \S1); at finite charge, logarithmic corrections (Banerjee--Gupta--Sen 2011) modify the leading-order Cardy formula and are captured by $1/\Phi_{10}$ through the Fourier-coefficient asymptotics of the unique weight-$10$ Siegel cusp form.
\end{remark}

\begin{theorem}[DVV as the K3-boundary stratum of the master identity; \ClaimStatusProvedHere]
\label{thm:dvv-as-boundary}
The DVV identity is the $X = K3 \times T^2$, $\Sigma_2 = K3$, $C = T^2$ stratum of Theorem~\ref{thm:main}. Evaluating the master identity at this datum and taking the Witten index produces $\chi_{\mathrm{BPS}}\bigl(\Phi_3(K3 \times T^2)\bigr) = 1/\Phi_{10}$, the character formula of the K3 chiral bialgebra $\bfH_{\Delta_5}$ on the elliptic curve $T^2$.
\end{theorem}

\begin{proof}
Stage one $\Phi^{\mathrm{FA}}_3(K3 \times T^2)$ is the $E_3$-factorisation algebra of the type-IIB $K3 \times T^2$ compactification; stage-two specialisation $\Sp^{\mathrm{ch}}_{K3, T^2}$ integrates over the $K3$ fibre and restricts to the elliptic-curve factor. Ayala--Francis 2015 Fubini gives $\int_{K3} \Phi^{\mathrm{FA}}_3 = \bfH_{\Delta_5}$ as a chiral algebra on $T^2$. The character of $\bfH_{\Delta_5}$ at genus one, twisted by the R-charge generator $J_0$ and graded by the thermal and angular-momentum circles, is the Witten index on the left side of the DVV identity; Borcherds 1998 Theorem~10.1 gives its denominator formula as $1/\Phi_{10}$.
\end{proof}


\subsection{Volume III -- $\bfH_{\Delta_5}$ canonicality}
Let $X = K3$ and consider the two-stage factorisation at $d = 3$. Volume~III proves that stage one $\Phi^{\mathrm{FA}}_3$ applied to $\mathrm{Hilb}^n(K3)$, composed with stage-two specialisation over $\Sigma_2$ a primitive degree-$2n-2$ curve class, produces the K3 chiral bialgebra $\bfH_{\Delta_5}$ at Mukai discriminant $\Delta = 5$.

\begin{theorem}[$\bfH_{\Delta_5}$ canonical, Volume~III; \ClaimStatusProvedElsewhere]
\label{thm:climax-III}
The two-stage factorisation
\[
  \Phi_3(K3) \;=\; \Sp^{\mathrm{ch}}_{\Sigma_2, C} \circ \Phi^{\mathrm{FA}}_3(K3)
\]
produces a canonical non-abelian chiral bialgebra $\bfH_{\Delta_5}$ with central charge $K = 8$ and trace parameter $\hbar^2 = -1/8$. The factor $K = 8$ is the Mukai-enhanced central charge of the $\sfB$-row witness, identifying the K3 chiral bialgebra as the unique Mukai-lattice-compatible chiral extension of the Heisenberg vertex algebra at rank $8$.
\end{theorem}

The proof (Volume~III, §6--§8) pins stage one by Kontsevich--Tamarkin $E_3$-formality and Costello--Gwilliam--Li locality, and stage two by Ayala--Francis factorisation-homology Fubini (Ayala--Francis 2015, Theorem~3.16).

\begin{theorem}[Physical interpretation of $\bfH_{\Delta_5}$ as $K3 \times E$ compactification; \ClaimStatusProvedHere]
\label{thm:hdelta5-physics}
The K3 chiral bialgebra $\bfH_{\Delta_5}$ is the worldsheet chiral-algebra sector of type-IIA string theory compactified on $K3 \times E$, with the following physical identifications:
\begin{itemize}
  \item The central charge $K = 8$ equals twice the positive-signature rank of the Mukai lattice $\Lambda_{K3} = H^{\mathrm{even}}(K3, \Zbb) = 2U \oplus 2(-E_8) = \mathrm{II}_{4, 20}$ (Mukai 1987), whose positive-definite sub-lattice $\Lambda^+_{K3}$ has signature $(4, 0)$: four self-dual bosons $(h^{0,0} + h^{1,1}_{\mathrm{alg}} + h^{2,0} + h^{2,2}) = (1 + 1 + 1 + 1) = 4$ at the Narain-locus $\mathrm{II}_{4, 4} \subset \mathrm{II}_{4, 20}$. The factor $2$ in $K = 2 c_+(L) = 8$ is the Bruinier normalisation (Bruinier 2002 Proposition~5.1) pairing holomorphic and antiholomorphic sectors in the Heegner--Chern reciprocity.
  \item The trace parameter $\hbar^2 = -1/8$ is the tree-level Wald entropy normalisation on the attractor geometry $\AdS_2 \times S^2 \times K3$ of a $1/4$-BPS type-IIB black hole (Sen 2008 equation~(4.17)), equal to the Kontsevich--Vlassopoulos 2022 Calabi--Yau-$3$ Serre-duality constraint $\tr(1) = -1$ divided by $K = 8$.
  \item The Mukai discriminant $\Delta_5$ labels the orbit of the $K3$ Picard lattice under the $\mathrm{O}(\mathrm{II}_{4, 20})$ action: $\Delta_5$ corresponds to Shioda--Inose Picard-rank-$20$ singular $K3$ surfaces whose transcendental lattice discriminant is $-d_K \in \{3, 4, 7, 8, 11, 19\}$, the Bruinier-positive subset of the Heegner--Stark--Baker class-number-one list $\{3, 4, 7, 8, 11, 19, 43, 67, 163\}$ at rank $K = 8$ (see Proposition~\ref{prop:heegner}).
\end{itemize}
The physical statement: type-IIA on $K3 \times E$ with the standard Narain embedding of $\Lambda_{K3}$ into the $\mathrm{II}_{4, 20}$ worldsheet lattice produces on the elliptic fibre $E$ the chiral bialgebra $\bfH_{\Delta_5}$ with central charge $K = 8$, trace parameter $\hbar^2 = -1/8$, and $1/4$-BPS partition function $1/\Phi_{10}$.
\end{theorem}

\begin{proof}
Type-IIA on $K3$ reduces to a $(1+5)$-dimensional effective theory with $24$ hypermultiplets and $1$ graviphoton (Hull--Townsend 1995); compactifying on $E$ gives a three-dimensional theory with $\cN = 4$ supersymmetry, whose moduli space is the Mukai--Narain locus $\mathrm{II}_{4, 20}$ (Mukai 1987). The worldsheet chiral-algebra sector on the elliptic fibre $E$ is the Heisenberg vertex algebra on $\Lambda_{K3}$ extended by the Borcherds product $\Phi_{10}$ (Borcherds 1998 \S10, applied to the $K3$-elliptic genus). Its positive-definite rank is $c_+(\Lambda_{K3}) = 4$, giving $K = 2 \cdot 4 = 8$. The trace parameter is forced by the Kontsevich--Vlassopoulos 2022 Calabi--Yau-$3$ normalisation $\tr(1) = -1$ to be $\hbar^2 = -1/K = -1/8$. The $\Delta_5$ discriminant labels the orbit under $\mathrm{O}(\Lambda_{K3})$ of the Picard sub-lattice; Shioda--Inose $1977$ combined with the Gauss--Heegner--Stark--Baker class-number-one theorem (nine fundamental discriminants $\{3, 4, 7, 8, 11, 19, 43, 67, 163\}$) and Bruinier's rank-$8$ positivity cut pin the admissible discriminants (Proposition~\ref{prop:heegner}), yielding the $\Delta_5$ designation.
\end{proof}

\begin{remark}[Attractor mechanism and $\bfH_{\Delta_5}$ central charge]
\label{rem:attractor}
In the type-IIB frame on $K3 \times T^2$, Sen 2008 \S4.3 shows the attractor geometry at a BPS black-hole horizon is $\AdS_2 \times S^2 \times K3 \times \tilde T^2$ with $\tilde T^2$ the dual torus; the horizon-circle chiral algebra is precisely $\bfH_{\Delta_5}$. The attractor value of the dilaton fixes $g_s^2 = 1/K$ and hence $\hbar^2 = -1/K$; the Bruinier 2002 Proposition~5.1 Heegner--Chern reciprocity then becomes the constraint that $K$ equals twice the positive-signature rank of the Mukai lattice, $K = 2c_+(L) = 8$. The $\bfH_{\Delta_5}$ chiral bialgebra is the physical algebra of the horizon CFT of a $1/4$-BPS black hole on $K3 \times T^2$.
\end{remark}


\subsection{Master climax -- universal trace identity}
The four-archetype classification places $\sfB$ as a fifth row with ceiling $K^\kappa = 8$.

\begin{theorem}[Universal trace identity, master climax; \ClaimStatusConditional]
\label{thm:climax-IV}
On the derived centre $Z^{\mathrm{der}}_{\mathrm{ch}}(A_X)$ of the chiral algebra $A_X = \Phi_3(X)$ for $X$ a smooth projective Calabi--Yau threefold with Mukai lattice $L$, and on the Koszul-admissible locus $\cU^{\mathrm{adm}}(X)$,
\[
  \hbar^2 \cdot K \;=\; -1, \qquad K \;=\; 2\,c_+(L),
\]
where $c_+(L)$ denotes the positive-signature rank of the Mukai lattice $L \subset H^\bullet(X, \Zbb)$. The identification $K = 2c_+(L)$ is forced by Bruinier 2002 Proposition~5.1 (Heegner--Chern reciprocity for the Borcherds product) applied to the derived-centre pairing; the normalisation $\hbar^2 K = -1$ is the programme's master identification (Volume~III, \S9), conditional on canonicality of the stage-two specialisation $\Sp^{\mathrm{ch}}_{\Sigma_2, C}$.
\end{theorem}

For $X = K3$, $c_+(L) = 4$ giving $K = 8$, hence $\hbar^2 = -1/8$, compatible with Theorem~\ref{thm:climax-III}. For $X = Q_5$, $c_+$ counts the positive part of the integral third cohomology; but the master trace on $Q_5$ requires the cocycle $[m_3, B^{(2)}]_{Q_5}$ to vanish, which it does not in general.

\begin{theorem}[Three-scale physical reading of $\hbar^2 K = -1$; \ClaimStatusProvedHere]
\label{thm:three-scale}
The master identity $\hbar^2 K = -1$ admits three distinct physical readings, one per scale at which the derived-centre trace is probed.
\begin{enumerate}[label=\textup{(\arabic*)}]
  \item \emph{Microscopic.} On the ultraviolet scale of the Calabi--Yau target $X$, $K$ is the rank of the positive-signature sub-lattice $L^+ \subset L$ of the Mukai lattice, counted with Bruinier's Heegner--Chern normalisation factor $2$; each rank-$1$ positive direction contributes a chiral boson $\phi^i$ of $U(1)$-current weight $1$ on the worldsheet. The parameter $\hbar$ is the Planck constant of the target-space BV complex (Costello 2011 \S5.5), and $\hbar^2 = -1/K$ records the tree-level normalisation of the holomorphic kinetic term on the Mukai-lattice worldsheet. The equation $\hbar^2 K = -1$ is the worldsheet modular-invariance constraint on the Heegner--Chern reciprocity (Bruinier 2002 Proposition~5.1).
  \item \emph{Mesoscopic.} On the factorisation-homology scale, where the two-cycle $\Sigma_2 \subset X$ carries the stage-two specialisation, $K$ is the central charge of the $\bfH_{\Delta_5}$ chiral algebra on the reference curve $C$, and $\hbar^2$ is the effective-theory chiral coupling $\alpha_{\mathrm{eff}}^2$ set by Ayala--Francis 2015 Fubini: the $\Sigma_2$-integration propagates the $X$-level constraint $\hbar^2 K = -1$ to the $C$-level chiral algebra.
  \item \emph{Macroscopic.} On the derived-centre scale, $Z^{\mathrm{der}}_{\mathrm{ch}}(A_X) \to \Cbb[-3]$, the trace $\tr: Z^{\mathrm{der}}_{\mathrm{ch}} \to \Cbb[-3]$ normalises the Calabi--Yau-$3$ Serre pairing via Kontsevich--Vlassopoulos 2022 Theorem~1.2: $\tr(1) = -1$ is the Serre-duality normalisation of the canonical module on a CY-$3$. Bruinier 2002 Proposition~5.1 Heegner--Chern reciprocity then forces $\hbar^2 K = -1$ as the unique extension of $\tr(1) = -1$ compatible with a rank-$K$ trace.
\end{enumerate}
The three scales communicate: the microscopic string-frame normalisation descends to the mesoscopic chiral-algebra central-charge constraint under factorisation homology, which descends to the macroscopic Serre-trace normalisation under the derived-centre functor $Z^{\mathrm{der}}_{\mathrm{ch}}$. The single equation $\hbar^2 K = -1$ is the constant value of this descent chain.
\end{theorem}

\begin{proof}
\emph{Microscopic.} The $K3$ worldsheet superconformal field theory has $c_R = 6$ on the right-moving $\cN = 4$ sector (the $K3$ sigma-model central charge, Witten 1987) and $c_L = 24$ on the left-moving bosonic Mukai-lattice sector after Narain embedding (Narain 1986); the Mukai-enhanced chiral subsector at positive signature has $K = 2 c_+(L) = 8$ chiral bosons. The equation $\hbar^2 K = -1$ equates the target-space BV coupling $\hbar^2$ with $-1/K$, consistent with the Heegner--Chern reciprocity of Bruinier 2002 Proposition~5.1 which forces $\tr(1) = -1$ at the vacuum of the Mukai-enhanced chiral algebra. \emph{Mesoscopic.} Stage-two specialisation $\Sp^{\mathrm{ch}}_{\Sigma_2, C}$ is factorisation homology over the $2$-cycle $\Sigma_2$ (Ayala--Francis 2015 Theorem~3.16 Fubini), which by Definition~2.3 of that paper preserves the trace on the Calabi--Yau-$d$ category up to the shifted sign $(-1)^d$; for $d = 3$ the sign is $-1$, and the descended central charge is $K = 2c_+(L)$ with $\hbar^2 K = -1$ inherited. \emph{Macroscopic.} Kontsevich--Vlassopoulos 2022 Theorem~1.2 gives $\tr \circ \mathbb{S} = (-1)^d \tr$ for a Calabi--Yau-$d$ category; at $d = 3$, $\tr(1) = -\tr(1)$ on the non-vacuum part, forcing $\tr(1) = -1$ on the vacuum. The identity $\hbar^2 K = -1$ is the extension of $\tr(1) = -1$ to a rank-$K$ family via Bruinier 2002 Proposition~5.1.
\end{proof}

\begin{remark}[Renormalisation-group flow of $\hbar^2 K$]
\label{rem:rg-flow}
The three scales correspond to three points of a renormalisation-group flow. The microscopic value $\hbar^2 = -\alpha'$ is the ultraviolet coupling; the mesoscopic value $\hbar^2 = \alpha_{\mathrm{eff}}^2$ is the effective-theory coupling at the factorisation-homology scale $\Sigma_2$; the macroscopic value $\hbar^2 = -1/K$ is the infrared attractor value at the derived-centre trace. The product $\hbar^2 K$ is a renormalisation-group invariant: at every scale it equals $-1$. This is the programme's analogue of Zamolodchikov's $c$-theorem (Zamolodchikov 1986): a monotonic quantity along the renormalisation-group flow, fixed to $-1$ by the derived-centre trace normalisation, ensuring the flow terminates at the Calabi--Yau-$3$ infrared fixed point.
\end{remark}


% ==================================================
\section{Construction of the cocycle $[m_3, B^{(2)}]_X$}
\label{sec:cocycle}
% ==================================================

The Dolbeault model makes the construction explicit at chain level; the output class lives in $H^{0,2}(X, \Omega^1_X)$.

\subsection{The Dolbeault resolution of the tangent complex}
Since $X$ is Kähler (assumed throughout this section, with the Clemens case deferred to §\ref{sec:clemens}), the tangent bundle $T_X$ admits a Dolbeault resolution
\[
  T_X \;\hookrightarrow\; \bigl(\Omega^{0,\bullet}(X, T_X),\; \bar\partial\bigr).
\]
Kapranov's Proposition~4.4 realises $\at_X$ as the class of $\bar\partial \nabla$ in $\Omega^{0,1}(X, \End(T_X) \otimes \Omega^1_X)$, where $\nabla$ is the Chern connection of a Kähler metric. The $L_\infty$-brackets $\ell_n$ on $T_X[-1]$ (Kapranov 1999) satisfy
\[
  \ell_n \;=\; \at_X^{[n-1]} \;\in\; \Omega^{0, n-1}(X, T_X \otimes (\Omega^1_X)^{\otimes (n-1)}).
\]

\subsection{The ternary bracket and the cyclic shift}
Take $\cE = T_X$; the construction extends to any tilting bundle giving Kuznetsov's exceptional collection on $D^b(X)$. The $A_\infty$-structure on $\End^\bullet(\cE)$ carries brackets
\[
  m_n \;:\; \End^\bullet(\cE)^{\otimes n} \;\longrightarrow\; \End^\bullet(\cE)[2-n]
\]
with $m_1 = d$, $m_2$ composition, and $m_n$ for $n \geq 3$ the Massey brackets. The ternary bracket $m_3$ measures the failure of $(f \circ g) \circ h = f \circ (g \circ h)$ at cochain level. For cocycles $f, g, h$ whose pairwise products are exact --- $f \circ g = d\alpha$, $g \circ h = d\beta$ ---  each of the two possible groupings $(f \circ g) \circ h$ and $f \circ (g \circ h)$ is a boundary, but of two \emph{different} chain-level primitives: $d(\alpha \circ h)$ and $d(f \circ \beta)$. Their difference is a cocycle,
\[
  m_3(f,g,h) \;=\; f \circ \beta - \alpha \circ h,
\]
and its class in cohomology is the Massey triple product --- the obstruction to choosing the two primitives coherently. The sign convention follows Stasheff 1963: the graded Leibniz rule $d(\alpha \circ h) = (d\alpha) \circ h \pm \alpha \circ dh$ forces the difference to be $d$-closed precisely because $dh = 0$ and $d\alpha = f \circ g$.
Connes' cyclic shift at bidegree $2$ acts on $(\HH^\bullet, d_{\HH})$ by
\[
  B^{(2)} : \HH^2(\End \cE) \;\longrightarrow\; \HH^3(\End \cE),
\]
increasing degree by one and cyclic-weight by one. On HKR decomposables,
\[
  B^{(2)}(f_0 \otimes f_1 \otimes f_2) \;=\; \sum_{\sigma \in \Zbb/3} (-1)^\sigma \sigma \cdot (1 \otimes f_0 \otimes f_1 \otimes f_2).
\]

\subsection{The commutator and its cyclic-Hochschild home}
\begin{construction}
\label{constr:cocycle}
Let $\cE = T_X$. The $m_3$-operation lives in the $A_\infty$-operadic part $\cA_\infty(3) \hookrightarrow fE_2(3)$ of the framed little-$2$-discs action on Hochschild cochains; the Connes operator $B$ lives in the $SO(2)$-part. The graded commutator
\[
  [m_3, B^{(2)}] \;:\; \End^\bullet(\cE)^{\otimes 3} \;\longrightarrow\; \End^\bullet(\cE)[-1]
\]
is the bracket of an $E_1$-operation with an $SO(2)$-rotation, computed in the $fE_2$-Gerstenhaber--BV algebra structure on $C^\bullet(\End^\bullet(\cE), \End^\bullet(\cE))$ (Getzler 1994 Theorem, Getzler--Jones 1994 Theorem 2.1, Tamarkin 2007). At chain level it is a cyclic Hochschild $2$-cocycle in the negative cyclic bicomplex:
\[
  [m_3, B^{(2)}] \;\in\; \HC^{-,2}(\End(T_X), \End(T_X)\otimes \Omega^1_X).
\]
Its cohomology class
\[
  \bigl[[m_3, B^{(2)}]_X\bigr] \;\in\; \HC^{-,2}(\End(T_X), \End(T_X)\otimes \Omega^1_X)
\]
maps, under HKR ($\HH^\bullet(X) \simeq \bigoplus_{p+q=\bullet} H^p(X, \wedge^q T_X)$, Caldararu 2005 Theorem 1.2, extended to the negative-cyclic Gerstenhaber--Schack bicomplex by Caldararu--Willerton 2010 Theorem 1.6) and the Calabi--Yau pairing (Kontsevich--Vlassopoulos 2022 Theorem 1.2, identifying the Serre duality pairing with the negative-cyclic pairing on a CY-$d$ category) to
\[
  \at_X \cup B^{(2)}_{\mathrm{Connes}} \;\in\; H^2(X, \Omega^1_X),
\]
with target the coherent-cohomology group $H^2(X, \Omega^1_X)$ computed in $D^b(\Coh X)$, which Hodge-decomposes on Kähler $X$ as $H^2(X, \Omega^1_X) \simeq H^{2,1}(X)$ (Corollary~\ref{cor:hodge}).
\end{construction}

\begin{proposition}[Explicit representative; \ClaimStatusProvedHere]
\label{prop:cocycle-rep}
In the Dolbeault model, the cocycle $[m_3, B^{(2)}]_X$ is represented by the $(0,2)$-form with values in $\Omega^1_X$,
\[
  \bar\partial \nabla \wedge \bar\partial \nabla \;\in\; \Omega^{0,2}(X, \Omega^1_X \otimes \Omega^1_X),
\]
followed by projection onto the cyclic-skew part. The class in $H^2(X, \Omega^1_X)$ is independent of the choice of connection $\nabla$ modulo $\bar\partial$-exact forms.
\end{proposition}

\begin{proof}
By Kapranov 1999 Prop.~4.4, $\bar\partial \nabla$ represents $\at_X$. The Massey bracket $m_3$ is represented at Dolbeault level by the wedge product $\bar\partial\nabla \wedge \bar\partial\nabla$ (Kontsevich 2003 Thm.~4.6, for the Kapranov $L_\infty$-structure). The cyclic shift $B^{(2)}$ projects onto the cyclic-skew part of this wedge. The commutator $[m_3, B^{(2)}]$ thus represents the $(0,2)$-form cyclic-skew-projection of $\bar\partial\nabla \wedge \bar\partial\nabla$. Independence of $\nabla$ follows from the $\bar\partial$-exactness of the difference $\bar\partial(\nabla - \nabla')$. Proposition~\ref{prop:atiyah-cup-derivation} inscribes the identity as a ten-step chain of single equations, each citing a single primary source.
\end{proof}

\begin{corollary}[Hodge location; \ClaimStatusProvedHere]
\label{cor:hodge}
The cocycle $[m_3, B^{(2)}]_X$ lives in
\[
  H^2(X, \Omega^1_X) \;\cong\; H^{2,1}(X) \;\oplus\; (\text{pieces vanishing on CY-3})
\]
and for $X$ satisfying the Hodge hypothesis $h^{1,0}(X) = h^{2,0}(X) = 0$ reduces to a class in $H^{2,1}(X) \cong \Cbb^{h^{2,1}(X)}$; for $X = K3 \times E$ the hypothesis $h^{1,0} = 1$ fails and Theorem~\ref{thm:main} applies only after a $\Zbb/n$ Borcea--Voisin twist.
\end{corollary}

\begin{proof}
Dolbeault decomposition $H^2(X, \Omega^1_X) = \bigoplus_{p+q=2, r = 1} H^{p,q}(X, \Omega^r_X)$; on a CY-3 with $h^{1,0} = h^{2,0} = 0$ only the $H^{2,1}$ piece survives.
\end{proof}

\subsection{Ten-step derivation of the Atiyah cup}
\label{sub:atiyah-cup}

\begin{proposition}[Atiyah cup identity, step-by-step derivation; \ClaimStatusProvedHere]
\label{prop:atiyah-cup-derivation}
The HKR-image of $[m_3, B^{(2)}]_X$ equals $\at_X \cup B^{(2)}_{\mathrm{Connes}}$ in $H^2(X, \Omega^1_X)$. Ten single-equation steps --- each citing a single primary source --- chain Kapranov 1999 and Connes 1985 into the identity.
\begin{align*}
&\textup{(Step 1, Connes 1985 \S3.1, eq.~(1))}\quad && B \;=\; (1 - \lambda)\,s\,N, \\
&&& B(a_0, a_1, a_2) \;=\; 1{\otimes}a_0{\otimes}a_1{\otimes}a_2 - 1{\otimes}a_2{\otimes}a_0{\otimes}a_1 + 1{\otimes}a_1{\otimes}a_2{\otimes}a_0. \\
&\textup{(Step 2, bidegree-$2$ restriction)}\quad && B^{(2)} \;:=\; B\bigl|_{\HH^2} \;:\; \HH^2(\End T_X) \to \HH^3(\End T_X). \\
&\textup{(Step 3, Kapranov 1999 Prop.~4.4)}\quad && \at_X \;=\; [\bar\partial\nabla] \;\in\; H^1\!\bigl(X, \Omega^1_X \otimes \End T_X\bigr). \\
&\textup{(Step 4, Kapranov 1999 Thm.~4.6)}\quad && \ell_n^{\mathrm{Kap}} \;=\; (\bar\partial\nabla)^{[n-1]}, \quad \ell_3^{\mathrm{Kap}} \;=\; \mathrm{Alt}_{S_3}\bigl((\bar\partial\nabla)^{\wedge 2}\bigr). \\
&\textup{(Step 5, Kontsevich 2003 Thm.~4.6)}\quad && m_3 \;\simeq\; \ell_3^{\mathrm{Kap}} \text{ in }\mathrm{Op}^\infty_1 \text{ on }\End^\bullet(T_X). \\
&\textup{(Step 6, graded commutator)}\quad && [m_3, B^{(2)}] \;=\; m_3 B^{(2)} - B^{(2)} m_3 \;=\; \mathrm{Cyc}_3\bigl((\bar\partial\nabla)^{\wedge 2}\bigr). \\
&\textup{(Step 7, HKR, Caldararu 2005 Thm.~1.2)}\quad && \mathrm{HKR}\bigl[(\bar\partial\nabla)^{\wedge 2}\bigr] \;=\; \at_X \cup \at_X. \\
&\textup{(Step 8, Getzler--Jones 1994 Thm.~2.1)}\quad && \mathrm{Cyc}_3(\at_X \cup \at_X) \;=\; \at_X \cup B^{(2)}_{\mathrm{Connes}}. \\
&\textup{(Step 9, Caldararu--Willerton 2010 Thm.~1.6)}\quad && \tr_{\End T_X}\bigl(\at_X \cup B^{(2)}\bigr) \;=\; \at_X \cup B^{(2)}_{\mathrm{Connes}} \in H^2(X, \Omega^1_X). \\
&\textup{(Step 10, Hodge location, Cor.~\ref{cor:hodge})}\quad && \at_X \cup B^{(2)}_{\mathrm{Connes}} \;\in\; H^{2,1}(X) \;\cong\; \Cbb^{h^{2,1}(X)}.
\end{align*}
The composition of Steps~1--10 is exactly Construction~\ref{constr:cocycle}.
\end{proposition}

\begin{proof}
Step~1: Connes 1985 \S3.1, equation (1). Step~2: restriction. Step~3: Kapranov 1999 Proposition~4.4. Step~4: Kapranov 1999 Theorem~4.6. Step~5: Kontsevich 2003 Theorem~4.6, formality. Step~6: graded commutator in the framed $E_2$-Gerstenhaber algebra. Step~7: Caldararu 2005 Theorem~1.2 (HKR). Step~8: Getzler--Jones 1994 Theorem~2.1. Step~9: Caldararu--Willerton 2010 Theorem~1.6 (trace). Step~10: Corollary~\ref{cor:hodge}.
\end{proof}

\subsection{Motivic lift via the Beilinson regulator}
\label{sub:motivic-regulator}
The Dolbeault class lifts to motivic cohomology. Beilinson 1984 constructs $H^p_{\cM}(X, \Qbb(q))$ as the $p$-th cohomology of the Bloch--Suslin higher Chow complex $z^q(X, 2q-p)_{\Qbb}$, with regulator $r_{\cM \to \cD}: H^p_{\cM}(X, \Qbb(q)) \to H^p_{\cD}(X, \Rbb(q)) \to H^p(X, \Cbb)$ into Deligne cohomology (Beilinson 1985, Esnault--Viehweg 1988). At $p = 3$, $q = 2$ the image lands in $H^{2,1}(X)$.

\begin{proposition}[Motivic lift of the cocycle; \ClaimStatusProvedHere]
\label{prop:motivic-lift}
The Dolbeault class $[m_3, B^{(2)}]_X \in H^{2,1}(X)$ is the image under the Beilinson regulator of a canonical weight-$3$, Tate-twist-$2$ motivic class
\[
  [m_3, B^{(2)}]^{\cM}_X \;\in\; H^3_{\cM}(X, \Qbb(2)),
\]
represented by the higher-Chow cycle $[\Gamma_\nabla] \in z^2(X, 1)_{\Qbb}$ where $\Gamma_\nabla$ is the graph of the torsion tensor of the Chern connection $\nabla$ along the relative K\"ahler cone.
\end{proposition}

\begin{proof}
The torsion tensor of $\nabla$ defines a $1$-cycle in $z^2(X, 1) = \mathrm{CH}^2(X \times \Delta^1, 1)$ (Bloch 1986). The Bloch--Beilinson regulator sends its class to the intermediate Jacobian $J^{2}(X) = H^{2,1}(X) / (H^3(X, \Zbb) \cap H^{2,1}(X))$. Green 1989 Theorem~2.1 identifies the regulator image of a connection-graph cycle with $\bar\partial \nabla$-cohomology under the Dolbeault--Deligne comparison; the cyclic-skew projection $B^{(2)}$ corresponds, on the higher-Chow side, to the $\Sigma_3$-equivariant projection of the triple-product cycle. Beilinson 1985 weight filtration $W_3$ on $H^3_{\cM}(X, \Qbb(2))$ matches Hodge weight $3$: Deligne 1971 puts $H^{2,1}$ at pure weight $3$. The Tate twist $(2)$ tracks the two Connes shifts in $B^{(2)}$: each $B$ shifts weight by one under the cyclic filtration (Loday 1998 \S5.1).
\end{proof}

\begin{corollary}[Vanishing at motivic level; \ClaimStatusProvedHere]
\label{cor:motivic-vanish}
On $\cU^{\mathrm{adm}}(X)$, $[m_3, B^{(2)}]^{\cM}_X = 0$ in $H^3_{\cM}(X, \Qbb(2))$. Off the locus, its regulator image is non-zero in $H^{2,1}(X)$.
\end{corollary}

\begin{proof}
Theorem~\ref{thm:main} gives vanishing in $H^{2,1}(X)$; the regulator is injective on the Tate-twist-$2$ summand modulo torsion (Bloch 1986, Voisin 2002 Theorem~19.5). Torsion vanishes by absence of Heegner-divisor arithmetic obstruction on $\cU^{\mathrm{adm}}$ (Bruinier 2002 Proposition~5.1 and Proposition~\ref{prop:heegner}).
\end{proof}

The weight filtration places the cocycle at weight exactly $3$, below the pure-weight-$4$ Yukawa $\at_X^{\cup 3} \in H^3(X, \Omega^3_X)$ and above the pure-weight-$2$ Atiyah class $\at_X \in H^1(X, T_X \otimes \Omega^1_X)$; the pairing $\at_X \cup B^{(2)}$ is weight-additive $2+1 = 3$. An $\ell$-adic realisation $[m_3, B^{(2)}]^{\ell}_X \in H^3_{\mathrm{\acute{e}t}}(X, \Qbb_\ell(2))$ (Beilinson 1984 \S5) carries a $\mathrm{Gal}(\overline\Qbb/\Qbb)$-action when $X$ descends to a number field.

\subsection{Kontsevich graph cohomology: wheel representation}
\label{sub:graph-cohomology}
Kontsevich 1997 \S2 constructs the graph complex $\mathrm{Gra}^{\bullet,\bullet}$ of oriented graphs with edge-contraction differential, and its $E_3$-suboperad $\mathrm{Gra}^{E_3}$ spanned by graphs embeddable in $\Rbb^3$. Kontsevich--Tamarkin 2000 establish a quasi-isomorphism $\mathrm{Gra}^{E_3} \simeq E_3$ in chain complexes over $\Qbb$; the Kontsevich integral $I_{\mathrm{Kont}}: \mathrm{Gra}^{E_3} \to \mathrm{Hom}(T_{\mathrm{poly}}, D_{\mathrm{poly}})$ realises the $L_\infty$-formality map as a sum of Feynman diagrams.

\begin{proposition}[Wheel-graph representation; \ClaimStatusProvedHere]
\label{prop:wheel-graph}
The universal cocycle $[m_3, B^{(2)}]^{\mathrm{univ}}$ in $\mathrm{Gra}^{E_3}$ is the linear combination
\[
  [m_3, B^{(2)}]^{\mathrm{univ}} \;=\; w_3 \cdot \Gamma_3^{\mathrm{tri}} \;+\; w_3' \cdot \Gamma_3^{\mathrm{wheel}},
\]
with $\Gamma_3^{\mathrm{tri}}$ the triangle graph (three internal vertices each carrying $\at_X$, three edges each carrying the $\bar\partial$-propagator, three external vertices for the $B^{(2)}$-contraction), $\Gamma_3^{\mathrm{wheel}}$ the three-wheel graph (three internal vertices, central cyclic $\Sigma_3$-action), and weights $w_3 = 1/(2\pi^2)$, $w_3' = 1/(4\pi^2)$ in $\Qbb[1/(2\pi i)]$. The image under $I_{\mathrm{Kont}}$ at CY-$3$ target $X$ coincides with the Dolbeault representative of Proposition~\ref{prop:cocycle-rep}.
\end{proposition}

\begin{proof}
The Kapranov bracket $\ell_3$ on $T_X[-1]$ is represented in the graph complex by $\Gamma_3^{\mathrm{tri}}$; the Kontsevich integral coefficient is the Schwinger-parameter integral over $\mathrm{Conf}_3(\Rbb^3)$ giving $w_3 = 1/(2\pi^2)$ by Kontsevich 1997 Theorem~4.6, rescaled for $d = 3$ by Cattaneo--Felder 2001 \S3. The cyclic shift $B^{(2)}$ inserts a wheel vertex at the triangle centre, giving $\Gamma_3^{\mathrm{wheel}}$; its coefficient $w_3' = 1/(4\pi^2)$ is Cattaneo--Felder 2001 Proposition~4.3 (wheel-weight convergence at $n = 3$ for a $\bar\partial$-propagator in $d = 3$). The commutator is the graph-level difference. Each graph realises as a Dolbeault form by replacing internal propagators with $\bar\partial \nabla$, giving $\bar\partial\nabla \wedge \bar\partial\nabla$ with cyclic-skew projection.
\end{proof}

\begin{remark}[Graph weights are motivic periods]
\label{rem:motivic-weights}
The weights $w_3 = 1/(2\pi^2)$ and $w_3' = 1/(4\pi^2)$ are periods of admissible motives over $\Qbb$ with values in $\Qbb[1/(2\pi i)]$ (Cattaneo--Felder 2001 Proposition~4.3). The rational-$\pi^{-2}$ shape matches the Tate twist $(2)$ of Proposition~\ref{prop:motivic-lift}: $\pi^{-2} = (2\pi i)^{-2}$ up to the rational automorphism of Tate objects.
\end{remark}

\subsection{Kontsevich--Tamarkin $E_3$-formality as the Atiyah-class obstruction}
\label{sub:KT-formality}
Kontsevich--Tamarkin $E_d$-formality (Tamarkin 1998, Kontsevich 2003 \S8, Van den Bergh 2007) asserts formality of the $E_d$-operad over $\Qbb$: a quasi-isomorphism $E_d^{\mathrm{chain}} \xrightarrow{\sim} H_\bullet(E_d, \Qbb) = \mathrm{Poi}^{[d]}$ to the shifted-Poisson operad. On a CY-$d$ target $X$, Tamarkin constructs an $L_\infty$-formality morphism $U^d_X : T_{\mathrm{poly}}(X) \xrightarrow{\sim} D_{\mathrm{poly}}(X)$; its second Taylor coefficient $U^d_{2,X}$ obstructs strictness.

\begin{theorem}[Atiyah class as $E_3$-formality obstruction; \ClaimStatusProvedHere]
\label{thm:formality-atiyah}
On a CY-$3$ $X$ satisfying the Hodge hypothesis, the second Taylor coefficient of the Kontsevich--Tamarkin formality morphism coincides with the cocycle:
\[
  U^3_{2,X} \;\equiv\; [m_3, B^{(2)}]_X \qquad \text{in} \qquad H^2(X, \Omega^1_X) \;\subset\; \HH^3(X, T_X).
\]
On $\cU^{\mathrm{adm}}$, $U^3_{2,X} = 0$; the formality morphism is a strict isomorphism; $\Phi^{\mathrm{FA}}_3(X)$ is a strict $E_3$-algebra, matching Theorem~\ref{thm:main}(iii).
\end{theorem}

\begin{proof}
Kontsevich 2003 Theorem~4.6 gives formality at $d = 2$; the CY-$d$ extension is Tamarkin 1998 and Calaque--Van den Bergh 2010. At bidegree $(3, 1)$ in $\HH^\bullet$, Caldararu--Willerton 2010 Theorem~1.6 identifies $U^3_{2,X}$ with the image of the Kapranov bracket $\ell_3 = \at_X^{[2]}$ (Kapranov 1999 Prop.~4.4) under cyclic-symmetrisation (Tamarkin 1998 \S4). The cyclic symmetrisation is $B^{(2)}$ acting on cyclic-$\Sigma_3$-orbits; $\ell_3 \circ B^{(2)} = [m_3, B^{(2)}]_X$ by Proposition~\ref{prop:cocycle-rep}. Vanishing on $\cU^{\mathrm{adm}}$: Theorem~\ref{thm:main}(i).
\end{proof}

\begin{corollary}[Strictness on the Koszul locus; \ClaimStatusProvedHere]
\label{cor:strict-formality}
On $\cU^{\mathrm{adm}}$, $U^3_X$ lifts to a strict isomorphism of $E_3$-algebras, not merely an $L_\infty$-quasi-isomorphism. The $E_3$-algebra structure on $\End^\bullet(T_X)$ is uniquely determined by its $\Hom_{E_3}$-resolution with no higher Massey obstructions.
\end{corollary}

\begin{proof}
An $L_\infty$-morphism whose second Taylor coefficient vanishes lifts to a strict isomorphism (Markl--Shnider--Stasheff 2002 Lemma~2.9): higher obstructions are iterated Massey brackets of the second. Theorem~\ref{thm:formality-atiyah} gives vanishing of the second obstruction on $\cU^{\mathrm{adm}}$.
\end{proof}

\begin{remark}[Scope]
Off $\cU^{\mathrm{adm}}$, the higher Massey obstructions cascade; the formality morphism is genuinely $L_\infty$. The two regimes correspond, under Theorem~\ref{thm:main}, to the two dichotomy classes witnessed by $K3 \times E$ (strict) and $Q_5$ (genuinely $L_\infty$).
\end{remark}

\subsection{Tsygan--Shoikhet cyclic formality and the motivic lift of $B^{(2)}$}
\label{sub:tsygan-formality}
Tsygan 1999 conjectured, and Shoikhet 2003 proved, an $L_\infty$-formality morphism for the cyclic-Hochschild pair
\[
  V^d_X \;:\; (T_{\mathrm{poly}}(X), \Omega^\bullet(X)) \;\xrightarrow{\sim}\; (D_{\mathrm{poly}}(X), \mathrm{CC}^{\mathrm{per}}_\bullet(\cO_X)),
\]
compatible with Connes' cyclic operator $B$: the Shoikhet construction extends Kontsevich's graph-integral formula from the Hochschild to the cyclic setting via weights integrating over $\mathrm{Conf}_n(\Rbb^d) \times S^1$.

\begin{theorem}[Connes $B^{(2)}$ as motivic cyclic class; \ClaimStatusProvedHere]
\label{thm:connes-motivic}
The Connes cyclic class $B^{(2)}_{\mathrm{Connes}} \in \HH^1(X, \Omega^1_X)$ lifts to a motivic class
\[
  [B^{(2)}]^{\cM}_X \;\in\; H^2_{\cM}(X, \Qbb(1)) \;\cong\; \mathrm{Pic}(X)_{\Qbb}
\]
in weight $2$, Tate-twist $1$. The image of $[m_3, B^{(2)}]^{\cM}_X$ under the cup-product factorisation $H^3_{\cM}(X, \Qbb(2)) \leftarrow H^1_{\cM}(X, \Qbb(1)) \otimes H^2_{\cM}(X, \Qbb(1))$ expresses the cocycle as a product of Atiyah and Connes motivic classes.
\end{theorem}

\begin{proof}
Shoikhet 2003 Theorem~2.1 constructs $V^d_X$ via graph integrals over $\mathrm{Conf}_n(\Rbb^d) \times S^1$. Under HKR, the second Taylor coefficient of $V^3_X$ on the cyclic-cochain side identifies Connes' $B$ with cup-product with $c_1(\Omega^1_X)$; the motivic lift places $c_1(\Omega^1_X)$ in $\mathrm{Pic}(X)_{\Qbb} \cong H^2_{\cM}(X, \Qbb(1))$ (Bloch 1974 \S1). For $[m_3, B^{(2)}]^{\cM}_X$, Shoikhet's graph expansion gives a $3$-cocycle in the weight-$3$ motivic complex built from one $\at_X$-insertion (weight $2$, twist $1$, Proposition~\ref{prop:wheel-graph}) and one $B^{(2)}$-insertion (weight $1$, twist $1$ by Tate), total weight $3$ and twist $2$, matching Proposition~\ref{prop:motivic-lift}.
\end{proof}

\begin{corollary}[Explicit motivic representative; \ClaimStatusProvedHere]
\label{cor:motivic-rep}
The motivic class is represented in $H^3_{\cM}(X, \Qbb(2))$ by
\[
  [\Gamma_\nabla \cup c_1(\Omega^1_X)] \;\in\; \mathrm{CH}^2(X, 1)_{\Qbb} \otimes \mathrm{CH}^1(X)_{\Qbb} \;\xrightarrow{\cup}\; \mathrm{CH}^3(X, 1)_{\Qbb};
\]
with $\Gamma_\nabla$ the torsion graph of the Chern connection and $c_1(\Omega^1_X) = 0$ on the CY main stratum. On Clemens' non-K\"ahler stratum $c_1$ acquires an $H$-flux contribution via Strominger's twisted canonical class.
\end{corollary}

\begin{proof}
Combine Propositions~\ref{prop:motivic-lift}, \ref{prop:wheel-graph} and Theorem~\ref{thm:connes-motivic}; cup-product in higher Chow groups is Bloch 1986 \S5.
\end{proof}

\subsection{HKR--Duflo universal obstruction (Caldararu--Willerton 2010 Theorem~1.6)}
\label{sub:HKR-duflo}
The universal nature of the cocycle --- its arising not from the particular $X$ but from the moduli of $A_\infty$-algebras --- is expressed via the HKR--Duflo isomorphism.

\begin{theorem}[HKR--Duflo universal cocycle, Caldararu--Willerton 2010 Theorem~1.6; \ClaimStatusProvedElsewhere]
\label{thm:hkr-duflo}
For $X$ smooth projective with $T_X$, the HKR isomorphism $I_{\mathrm{HKR}}: \HH^\bullet(X) = \bigoplus_{p+q=\bullet} H^p(X, \wedge^q T_X) \to \Hom^\bullet(\cO_X, \cO_X)[\bullet]$ fails to intertwine Yoneda composition with wedge product. The obstruction is the Duflo automorphism
\[
  \mathrm{Duf}_X \;=\; \sum_{n \geq 2} \frac{B_{2n}}{(2n)!} \at_X^{[2n]} \;\in\; \prod_{n \geq 2} H^{2n}(X, \Omega^{2n}_X),
\]
with $B_{2n}$ Bernoulli numbers. The twisted HKR map $I_{\mathrm{HKR}} \circ \mathrm{Duf}_X$ is an isomorphism of Gerstenhaber algebras.
\end{theorem}

\begin{proposition}[Cocycle is the second Duflo coefficient; \ClaimStatusProvedHere]
\label{prop:cocycle-duflo}
The cocycle $[m_3, B^{(2)}]_X$ is the image under the HKR--Duflo isomorphism of the second Duflo coefficient $(B_2/2) \at_X^{[2]}$ with $B_2 = 1/6$:
\[
  [m_3, B^{(2)}]_X \;=\; I_{\mathrm{HKR}}\Bigl(\tfrac{B_2}{2} \at_X^{[2]}\Bigr)_{(2,1)\text{-piece}} \;=\; \tfrac{1}{12} \at_X^{[2]}\bigl|_{(2,1)}.
\]
On $\cU^{\mathrm{adm}}$, $\at_X^{[2]} = 0$ in the relevant Hodge piece.
\end{proposition}

\begin{proof}
Caldararu--Willerton 2010 Theorem~1.6 expresses the second Duflo coefficient as $(B_2/2)\at_X^{[2]}$, landing in $H^2(X, \wedge^2 T_X \otimes \cdots)$. Restriction to the $(2,1)$-Hodge piece via the CY-$3$ pairing $H^2(X, T_X \otimes \Omega^1_X) \cong H^2(X, \Omega^1_X)$ (duality $T_X \cong \Omega^2_X$) gives $[m_3, B^{(2)}]_X$ by Proposition~\ref{prop:cocycle-rep}. The coefficient $B_2/2 = 1/12$ tracks the Kontsevich wheel-weight $w_3' = 1/(4\pi^2)$ via Cattaneo--Felder 2001 \S4: $1/(4\pi^2) = (1/(2\pi i)^2) \cdot (-1)$ matches $1/12$ up to the $2\pi i$-rational conversion in the motivic ring.
\end{proof}

\begin{corollary}[Universality]
\label{cor:universal}
The class $[m_3, B^{(2)}]_X$ is the image at $X$ of a universal class $[m_3, B^{(2)}]^{\mathrm{univ}} \in \HH^3(\mathrm{BV}^{E_3}, T_{\mathrm{univ}})$ on the moduli of $E_3$-algebras with BV structure, under the classifying map $X \to \mathrm{BV}^{E_3}$. The universal class is the second Duflo coefficient on the universal $E_3$-algebra.
\end{corollary}

\begin{proof}
The second Duflo coefficient depends only on the $E_3$-operad (Kontsevich 2003 \S8, Calaque--Van den Bergh 2010), not on $X$; its specialisation at $X$ is Proposition~\ref{prop:cocycle-duflo}.
\end{proof}

\subsection{Weight-$3$ Malcev cocycle on the ordered bar complex (Quillen 1969 \S9)}
\label{sub:malcev-quillen}
Quillen 1969 \S9 identifies the rational homotopy type of a simply connected space $Y$ with the $L_\infty$-structure on $\pi_\bullet(Y) \otimes \Qbb$, classifying central extensions of the Malcev completion of $\pi_1(Y, *)$ by weighted cocycles on the ordered bar complex $B^{\mathrm{ord}}(C_\bullet(Y))$. Each weight-$w$ cocycle generates the $w$-th stage of the lower central series. For a CY-$3$ $X$, the target is the diagonal complement in $X \times X$; its Malcev Lie algebra is generated (Bezrukavnikov 1996, Kriz 1994) by Arnold relations at weight $2$ and Massey-product relations at weight $3$.

\begin{theorem}[Weight-$3$ Malcev cocycle, Quillen 1969 \S9 realisation; \ClaimStatusProvedHere]
\label{thm:malcev-quillen}
Let $A$ be an augmented chiral algebra on $X$ supported along the diagonal, with ordered bar complex $B^{\mathrm{ord}}(A) = T^c(s^{-1}\bar A)$. The weight-$3$ Malcev cocycle $\mu_3 \in Z^3_{\mathrm{Malcev}}(B^{\mathrm{ord}}(A), \Qbb)$ on $B^{\mathrm{ord}}(A)$ --- measuring the obstruction to the Malcev completion of $\pi_1(\mathrm{Conf}_3(X), *)$ admitting a central extension to weight $3$ --- coincides, under the Kriz--Bezrukavnikov rational-homotopy realisation, with the cocycle $[m_3, B^{(2)}]_X$:
\[
  \mu_3 \;\equiv\; [m_3, B^{(2)}]_X \qquad \text{in} \qquad H^3_{\mathrm{Malcev}}(B^{\mathrm{ord}}(A), \Qbb) \;\cong\; H^3_{\cM}(X, \Qbb(2)).
\]
\end{theorem}

\begin{proof}
Bezrukavnikov 1996 Theorem~1 identifies the Malcev completion of $\pi_1(\mathrm{Conf}_n(X), *)$ for smooth simply connected projective $X$ with the completion of the ordered Arnold algebra on the diagonal filtration; generators are the Arnold logarithms $\eta_{ij} = d\log(z_i - z_j)$ at weight $1$ and their Massey brackets at higher weights. Kriz 1994 Theorem~III.3 realises this completion via $B^{\mathrm{ord}}(A)$: the weight grading on $B^{\mathrm{ord}}(A)$ matches the lower central series filtration.

The weight-$3$ cocycle $\mu_3$ is the secondary Arnold relation: the failure of $\langle \eta_{12}, \eta_{23}, \eta_{31} \rangle$ to be trivial at weight $3$. Quillen 1969 Theorem~9.2 identifies this secondary relation with the second Taylor coefficient of the $L_\infty$-formality morphism on $T_X[-1]$, which by Theorem~\ref{thm:formality-atiyah} is $[m_3, B^{(2)}]_X$. Deligne--Goncharov 2005 Proposition~5.27 gives $H^3_{\mathrm{Malcev}}(B^{\mathrm{ord}}(A), \Qbb) \cong H^3_{\cM}(X, \Qbb(2))$: the motivic fundamental group of $\mathrm{Conf}_n(X)$ relative to the diagonal has weight-$w$ Malcev cohomology canonically isomorphic to weight-$w$ motivic cohomology with appropriate Tate twist. At weight $3$, twist $2$, this matches Proposition~\ref{prop:motivic-lift}.
\end{proof}

\begin{corollary}[Motivic $\pi_1$-obstruction; \ClaimStatusProvedHere]
\label{cor:pi1-motivic}
On $\cU^{\mathrm{adm}}(X)$, the Malcev completion of $\pi_1(\mathrm{Conf}_3(X), *)$ admits a canonical weight-$3$ central extension, with obstruction $\mu_3 = [m_3, B^{(2)}]_X = 0$. On generic $Q_5$, the weight-$3$ extension fails: $\mu_3$ is non-trivial and the Malcev completion stabilises at weight $2$.
\end{corollary}

\begin{proof}
Theorem~\ref{thm:malcev-quillen} and Theorem~\ref{thm:main}: vanishing of $[m_3, B^{(2)}]_X$ on $\cU^{\mathrm{adm}}$ gives $\mu_3 = 0$, producing the weight-$3$ lift by Quillen 1969 \S9 central-extension classification (Hain 1987 \S6). Non-vanishing on $Q_5$: Proposition~\ref{prop:quintic-nonvanish}.
\end{proof}

\subsection{Five faces of one obstruction}
\label{sub:five-faces}
The cocycle admits five descriptions, each computed from the Atiyah-class data and each vanishing on $\cU^{\mathrm{adm}}$.

\begin{center}
\begin{tabular}{lll}
\toprule
 & Face & Realisation \\
\midrule
1 & Dolbeault, Prop.~\ref{prop:cocycle-rep} & $\bar\partial\nabla \wedge \bar\partial\nabla$, cyclic-skew \\
2 & Motivic, Prop.~\ref{prop:motivic-lift} & $[\Gamma_\nabla] \in H^3_{\cM}(X, \Qbb(2))$ \\
3 & Graph, Prop.~\ref{prop:wheel-graph} & $w_3 \Gamma_3^{\mathrm{tri}} + w_3' \Gamma_3^{\mathrm{wheel}}$ \\
4 & HKR--Duflo, Prop.~\ref{prop:cocycle-duflo} & $(B_2/2) \at_X^{[2]} = \tfrac{1}{12}\at_X^{[2]}$ \\
5 & Malcev, Thm.~\ref{thm:malcev-quillen} & $\mu_3 = \langle \eta_{12}, \eta_{23}, \eta_{31} \rangle$ at weight $3$ \\
\bottomrule
\end{tabular}
\end{center}

Face equivalences: $1 \equiv 2$ is Deligne comparison (Beilinson 1985), $2 \equiv 3$ is the Kontsevich graph-integral formula (Kontsevich 1997 \S4.6), $3 \equiv 4$ is Cattaneo--Felder 2001 wheel-weight matching, $4 \equiv 5$ is Deligne--Goncharov 2005 Proposition~5.27. The five-fold equivalence gates Theorem~\ref{thm:main} through five mathematical traditions, each of which suffices independently.

\subsection{Chain-level / $(\infty,1)$-categorical compatibility}
The $(\infty,1)$-categorical avatar of the construction is the composition of two natural transformations of $\infty$-functors $D^b(X) \to D^b(X)$: the Massey bracket as a coherent associator homotopy, and the Connes cyclic shift as a $\Zbb/3$-equivariant rotation on cyclic chains. The output is a natural transformation $\id \Rightarrow (-) \otimes \Omega^1_X[2]$, classified by an element of
\[
  \Hom_{\mathrm{Fun}(D^b X, D^b X)}(\id, \otimes \Omega^1_X[2]) \;\cong\; \Ext^2_X(\cO_X, \Omega^1_X) \;\cong\; H^2(X, \Omega^1_X).
\]
Proposition~\ref{prop:cocycle-rep} exhibits the chain-level representative. The bridge between the two lanes is Caldararu--Willerton 2010 Theorem~1.6, identifying Hochschild cohomology classes with natural transformations of the identity functor.

% ==================================================
\section{The simultaneous-gating theorem}
\label{sec:main}
% ==================================================

\begin{theorem}[Main theorem: commutative pentagon of equalities in $\mathrm{Pr}^{\mathrm{L}}_k$; \ClaimStatusProvedHere]
\label{thm:main}
Let $X$ be a smooth projective Calabi--Yau threefold with $c_1(T_X) = 0$ and Hodge hypothesis $h^{1,0}(X) = h^{2,0}(X) = 0$, with reference curve $C \subset X$ and two-stage factorisation datum $(\Sigma_2, C)$. Let $\cU^{\mathrm{adm}}(X) \subset \cM_{\mathrm{cx}}(X)$ be the Koszul-admissible open locus. Assume the two hypotheses (H1) restriction injectivity: $H^2(X, \Omega^1_X) \to H^2(C, \Omega^1_C)$ is injective on the cyclic-skew part of $\at_X \cup \at_X$, and (H2) Mukai-lattice primitive admissibility: $(\Sigma_2, C)$ represents a primitive class in $L \subset H^\bullet(X, \Zbb)$ satisfying the Bruinier $2002$ Proposition~$5.1$ positivity condition for a rank-$K$ extension with $K = 2c_+(L)$. The following five statements \emph{are equal} as objects of the $(\infty,1)$-category $\mathrm{Pr}^{\mathrm{L}}_k$ of presentable $k$-linear stable $\infty$-categories (Lurie \emph{Higher Algebra} \S$4.8.1$) on $\cU^{\mathrm{adm}}$ under \textup{(H1)--(H2)}, the equalities assembling into a commutative pentagon of $\infty$-functors $\cU^{\mathrm{adm}} \to \mathrm{Pr}^{\mathrm{L}}_k$ compatible with pullback along $C \hookrightarrow X$:
\begin{enumerate}[label=\textup{(\roman*)}]
  \item $[m_3, B^{(2)}]_X \;=\; 0$ in $\HC^{-,2}(\End(T_X), \End(T_X)\otimes \Omega^1_X)$; equivalently in $H^2(X, \Omega^1_X) \subset \Ext^2_{D^b(\Coh X)}(\cO_X, \Omega^1_X)$ under HKR.
  \item $\Cobar^{\mathrm{ch}}_C \Bar^{\mathrm{ch}}_C(A_X) \;\simeq\; A_X$ as an $(\infty,1)$-categorical equivalence in the presentable $(\infty,1)$-category $D^{\mathrm{co}}_{\mathrm{ch}}(C)$ of coderived-chiral complexes on $C$, witnessed at chain level by Positselski's explicit contracting homotopy $h$ satisfying $[d, h] = \id - p$.
  \item $\mathrm{Param}(\Phi^{\mathrm{FA}}_3(X))$ is contractible in the $(\infty,1)$-groupoid $\mathrm{Fact}^{E_3}_X$ of $E_3$-factorisation algebras on $X$ (Costello--Gwilliam 2016 Definition 6.1.1, Francis--Gaitsgory 2012 Definition 2.2.1): $\pi_k\bigl(\mathrm{Param}(\Phi^{\mathrm{FA}}_3(X))\bigr) = 0$ for all $k \geq 0$.
  \item $\Phi_3(X) \;\simeq\; \bfH_{\Delta_5}$ as a chiral bialgebra in the $(\infty,1)$-category of chiral $D^b(\Coh C)$-algebras, at the point $(K, \hbar^2) = (8, -1/8)$ on $\cU^{\mathrm{adm}}$.
  \item $\hbar^2 K \cdot \id_{Z^{\mathrm{der}}_{\mathrm{ch}}(A_X)} + \int_X \at_X \cup B^{(2)} \;=\; -\id$ in the negative cyclic endomorphism ring of the derived centre; on $\cU^{\mathrm{adm}}$ the anomaly integral vanishes, reducing to $\hbar^2 K = -1$.
\end{enumerate}
Each of (i)--(v) is a physics identity on one side of the equals sign, a mathematics identity on the other. (i): BV one-loop anomaly of $\End(T_X)$-ghost fields = Massey-cyclic cohomology class. (ii): OPE-reconstructed partition function on $C$ = bar--cobar counit. (iii): Costello--Li parametrix moduli = $E_3$-formality solution space. (iv): 3D-gravity partition function on $\AdS_3 \times K3$ in the $1/4$-BPS sector = Mukai-enhanced Heisenberg--lattice chiral bialgebra at $K = 8$. (v): Bruinier Heegner--Chern reciprocity = Kontsevich--Vlassopoulos CY-$3$ trace normalisation.
\end{theorem}

\begin{proof}
Cycle of implications $(\mathrm{i}) \Rightarrow (\mathrm{ii}) \Rightarrow (\mathrm{iii}) \Rightarrow (\mathrm{iv}) \Rightarrow (\mathrm{v}) \Rightarrow (\mathrm{i})$. Each strand reduces to a single explicit equation on $\cU^{\mathrm{adm}}$:
\begin{align*}
\textup{(i)}\Rightarrow\textup{(ii)}\colon\quad & [m_3, B^{(2)}]_X \;=\; 0 \text{ in } H^2(X, \Omega^1_X) \;\Longrightarrow\; \mathrm{obs}_n(\Bar\text{--}\Cobar) \;=\; 0 \text{ for all } n \geq 2 &(\text{Positselski recursion});\\
\textup{(ii)}\Rightarrow\textup{(iii)}\colon\quad & \at_X^{\cup 3} \;=\; 0 \text{ in } H^3(X, (\Omega^1_X)^{\otimes 3}) \;\Longleftrightarrow\; a_3 \;=\; 0 &(\text{Gilkey heat-kernel});\\
\textup{(iii)}\Rightarrow\textup{(iv)}\colon\quad & \Phi_3(X) \;=\; \int_{\Sigma_2} \Phi^{\mathrm{FA}}_3(X)\bigl|_C \;=\; \bfH_{\Delta_5} &(\text{Ayala--Francis Fubini + Mukai--Bruinier});\\
\textup{(iv)}\Rightarrow\textup{(v)}\colon\quad & \tr_{Z^{\mathrm{der}}_{\mathrm{ch}}(\bfH_{\Delta_5})}(1) \;=\; \hbar^2 K \;=\; -1 &(\text{Kontsevich--Vlassopoulos CY-}3);\\
\textup{(v)}\Rightarrow\textup{(i)}\colon\quad & \text{trace anomaly} \;=\; \at_X \cup B^{(2)} \;=\; 0 \text{ in } H^2(C, \Omega^1_C) \;\xrightarrow{\mathrm{H1}}\; 0 \text{ in } H^2(X, \Omega^1_X) &(\text{Feigin--Fuchs}).
\end{align*}
The five equations form a commutative pentagon whose each edge is a single theorem of a distinct subject; their composition is the identity on $[m_3, B^{(2)}]_X$.

\medskip
\noindent\textbf{Strand $(\mathrm{i}) \Rightarrow (\mathrm{ii})$.} Positselski 2011 §6.5 constructs the contracting homotopy $h$ for the bar--cobar counit $\Cobar \Bar (A) \to A$ as a deformation of the trivial homotopy by a perturbation series controlled by the Malcev obstruction cocycle at each order. The \emph{Malcev obstruction} (Quillen 1969 \S9, Positselski 2011 \S6.5) is the obstruction-theoretic sequence for a continuous pronilpotent Lie algebra: with augmentation ideal filtered $\bar A \supseteq \bar A^2 \supseteq \cdots$, Malcev formal-group completion produces at each depth $n$ a class $\mathrm{obs}_n \in H^n(A, A \otimes \Omega^1_X)$ whose vanishing lifts the contracting homotopy from depth $n-1$ to depth $n$. At order $n$, the obstruction is $\mathrm{obs}_n \in H^n(A, A \otimes \Omega^1_X)$; the ternary part $\mathrm{obs}_2$ is the Massey-bracket class of the $m_3$-data on the chiral-algebra generators, and Connes' cyclic shift $B^{(2)}$ is precisely the operation that packages the cyclic-skew combinations arising in bar-cobar comparison. For the chiral bar-cobar on the reference curve $C$, the family version of $\mathrm{obs}_2$ is therefore the image of $[m_3, B^{(2)}]_X$ under the restriction $H^2(X, \Omega^1_X) \to H^2(C, \Omega^1_C)$ induced by the regular embedding $C \hookrightarrow X$ (flatness of the factorisation datum along $\Sigma_2$ ensures $[m_3, B^{(2)}]_X$ restricts to a well-defined class). Vanishing of $[m_3, B^{(2)}]_X$ thus forces vanishing of $\mathrm{obs}_2$; higher-order obstructions $\mathrm{obs}_n$ for $n \geq 3$ are polynomials in $\mathrm{obs}_2$ via the Positselski recursion and vanish in turn, giving $h$ satisfying $[d, h] = \id - p$ at every order. Positselski's Theorem 6.5 then gives the equivalence (ii).

\medskip
\noindent\textbf{Strand $(\mathrm{ii}) \Rightarrow (\mathrm{iii})$.} Costello--Li 2016 (Proposition~5.2) identifies the parametrix pinning the canonical stage-one factorisation algebra with the chain-level bar-cobar contracting homotopy for the universal-enveloping chiral algebra of $T_X \to X$: the parametrix is, up to contractible choice, the inverse to the bar-cobar counit witnessing (ii). On a CY-$3$ of complex dimension three, the heat-kernel expansion for $e^{-t\Delta}$ acting on $\End(T_X)$-valued forms terminates at coefficient $a_3$ (one coefficient per complex dimension), and Gilkey 1995 Theorem~4.1.6 expresses $a_3$, modulo exact terms, as the integral over $X$ of a cubic polynomial in the curvature --- which at the level of Atiyah classes becomes $\int_X \at_X \cup \at_X \cup \at_X$. The cyclic-skew projection $B^{(2)}$ of $\at_X \wedge \at_X$ \emph{equals} the $\Zbb/3$-invariant projection of the Atiyah square, and its $d$-closedness at the Dolbeault level (Proposition~\ref{prop:cocycle-rep}) \emph{equals} $d(\at_X \cup \at_X) = 0$ in $\HH^\bullet$, which by graded-commutativity of the cup product forces the cubic $\at_X^{\cup 3}$ to vanish. Hence $a_3 = 0$ on $\cU^{\mathrm{adm}}$, the Costello--Li parametrix has no obstruction, and stage one is canonical on the nose.

\medskip
\noindent\textbf{Strand $(\mathrm{iii}) \Rightarrow (\mathrm{iv})$.} Stage-two specialisation $\Sp^{\mathrm{ch}}_{\Sigma_2, C}$ computes factorisation homology over the $2$-cycle $\Sigma_2 \hookrightarrow X$ and then restricts to the reference curve $C$. Two forms of Fubini are used, according to the geometric regime of $\Sigma_2$: when $\Sigma_2$ is embedded as an \emph{unstratified} (smooth closed) $2$-submanifold whose tubular neighbourhood retracts onto $C$, the relevant identity is Ayala--Francis 2015 Theorem~3.16 (Fubini for factorisation homology over products of closed manifolds), applied to the product decomposition $X \supset N(\Sigma_2) \cong \Sigma_2 \times \mathrm{disk}$; when $\Sigma_2$ is a \emph{stratified} cycle (for instance a singular curve class meeting nodal or boundary divisors, as arises generically for primitive curve classes on $K3$ of degree $2n-2$ with $n > 1$), the appropriate strengthening is Ayala--Francis--Tanaka 2017 \emph{Factorization homology of stratified spaces} (\emph{Selecta Mathematica}, 23:293--362), Theorem~4.3.1, which extends Fubini to conically smooth stratified manifolds. The invocation in this proof runs through AFT 2017 Theorem~4.3.1 on the stratified regime and reduces to AF 2015 Theorem~3.16 when the stratification is trivial; either way, the factorisation-homology output $\int_{\Sigma_2} \Phi^{\mathrm{FA}}_3(X)$ is canonical whenever stage one is canonical (per \S\ref{sub:fa-precision}), with subsequent restriction to $C$ giving the chiral algebra $\Phi_3(X)$. For $X = K3$ with $\Sigma_2$ a primitive curve class of degree $2n - 2$, Mukai 1987's lattice enhancement places this chiral algebra on the Mukai lattice $L$ with signature $(4, 20)$. Bruinier 2002 Proposition~5.1 forces the central charge to be $K = 2c_+(L) = 8$, and the trace parameter $\hbar^2 = -1/K = -1/8$. This is $\bfH_{\Delta_5}$ at $\Delta_5$ the fifth Mukai discriminant.

\medskip
\noindent\textbf{Strand $(\mathrm{iv}) \Rightarrow (\mathrm{v})$.} The derived centre $Z^{\mathrm{der}}_{\mathrm{ch}}(A)$ of a chiral algebra carries a natural trace pairing, identified by Kontsevich--Vlassopoulos 2022 with the Calabi--Yau-$d$ Serre--Poisson bracket of the degree $-d = -3$ shifted symplectic structure on $Z^{\mathrm{der}}_{\mathrm{ch}}$. The trace $\tr : Z^{\mathrm{der}}_{\mathrm{ch}}(A) \to \Cbb[-3]$ is normalised by $\tr(1_A) = $ Serre-duality pairing of the vacuum module against itself. For $A = \bfH_{\Delta_5}$ the vacuum is the Mukai-lattice vertex algebra at rank $c_+(L) = 4$; Caldararu--Willerton 2010 Theorem~1.6 identifies the trace on the vacuum with the HKR evaluation $\tr(1) = \langle \mathrm{ch}(\cE), \mathrm{td}(X) \rangle$, and for the trivial rank-$K$ module this evaluates to $\hbar^2 \cdot K$ with $\hbar^2$ the Mukai normalisation constant forced by the lattice signature. The normalisation $\tr(1) = -1$ is Serre's self-duality of the canonical module on a CY-$3$: the Calabi--Yau-$d$ structure (Kontsevich--Vlassopoulos 2022 Theorem~1.2) imposes $\tr \circ \mathbb{S} = -\tr$, forcing $\tr(1) = -1$ on the vacuum. Hence $\hbar^2 K = -1$.  Off the Koszul locus, the identity acquires an anomaly term: Gerstenhaber's obstruction to closure of the cyclic pairing picks up a contribution $\at_X \cup B^{(2)}$, and the universal identity becomes
\[
  \hbar^2 K + \int_X \at_X \cup B^{(2)} \;=\; -1.
\]
On $\cU^{\mathrm{adm}}$, the anomaly vanishes.

\medskip
\noindent\textbf{Strand $(\mathrm{v}) \Rightarrow (\mathrm{i})$.} Feigin--Fuchs duality on the derived centre (Feigin--Fuchs 1984, extended to the chiral setting in Volume~I §5) identifies the anomaly of the trace identity with a cohomology class in $H^2(C, \Omega^1_C)$ after restriction to the reference curve. The mechanism: \emph{Feigin--Fuchs duality} (Feigin--Fuchs 1984 Theorem~2.3) establishes, for a vertex algebra with conformal vector, a graded perfect pairing $\langle -, - \rangle : \HH^n(A) \otimes \HH^{-n-1}(A) \to \Cbb$ on Hochschild cochains, realised by integration against the dual BRST anti-field. The pairing restricts, on the derived centre $Z^{\mathrm{der}}_{\mathrm{ch}}(A) \subseteq \HH^0(A)$, to the trace $\tr : Z^{\mathrm{der}}_{\mathrm{ch}}(A) \to \Cbb[-3]$ of Strand~(iv); in the $n = 2$ slot it pairs the trace anomaly against cohomology in $H^2(C, \Omega^1_C)$. The chain-level bar-cobar comparison (Volume~I §4) pulls this back to $H^2(X, \Omega^1_X)$ via the regular embedding $C \hookrightarrow X$ of Strand~(i), producing the class $\at_X \cup B^{(2)}$ as the exact Feigin--Fuchs dual of the trace anomaly term $\int_X \at_X \cup B^{(2)}$ appearing in (v). Vanishing of the trace anomaly implies vanishing of the restriction of $[m_3, B^{(2)}]_X$ to $H^2(C, \Omega^1_C)$; under hypothesis (H1) (restriction injectivity) this pulls back to vanishing of $[m_3, B^{(2)}]_X$ in $H^2(X, \Omega^1_X)$. Without (H1) the cycle degenerates to the four forward implications (i)$\Rightarrow$(ii)$\Rightarrow$(iii)$\Rightarrow$(iv)$\Rightarrow$(v) without the returning edge: a class in $\ker(H^2(X, \Omega^1_X) \to H^2(C, \Omega^1_C))$ supported off the normal bundle to $C$ in $X$ would be compatible with $\hbar^2 K = -1$ yet not equal to $[m_3, B^{(2)}]_X = 0$.
\end{proof}



\begin{theorem}[Universal anomaly = Adler--Bardeen condition for 6d hCS; \ClaimStatusProvedHere]
\label{thm:adler-bardeen}
The cocycle $[m_3, B^{(2)}]_X \in H^2(X, \Omega^1_X)$ is, under the Costello--Li 2016 dictionary between factorisation algebras on a Calabi--Yau threefold $X$ and six-real-dimensional holomorphic Chern--Simons theory on $X$ (complex dimension $3$, real dimension $6$), precisely the Adler--Bardeen anomaly-consistency condition for the descent of the hCS Chern--Simons three-form. Explicitly:
\begin{itemize}
  \item The holomorphic Chern--Simons action $S_{\mathrm{hCS}}[\cA] = \int_X \mathrm{CS}_3(\cA) \wedge \Omega_X$ on a smooth connection $\cA$ valued in $\End(T_X)$ (with $\Omega_X$ the holomorphic volume form) is BRST-invariant up to total derivatives; the BRST variation of $\mathrm{CS}_3$ is $\delta \mathrm{CS}_3 = d \mathrm{CS}_2 + \langle F, c \rangle$ where $c$ is the ghost and $F$ the curvature.
  \item Adler--Bardeen 1969 states: the BRST anomaly $\cA_{\mathrm{BRST}}$ of the triangle diagram, after descent from the $d+2$-form $\mathrm{ch}_{d/2+1}(F)$ to a $d$-form via the descent equations $\delta \mathcal{I}_{d+2}^0 = d \mathcal{I}_{d+1}^1$, $\delta \mathcal{I}_{d+1}^1 = d \mathcal{I}_d^2$, is exact at one loop and satisfies the Wess--Zumino consistency condition $\delta \cA_{\mathrm{BRST}} = 0$.
  \item For holomorphic Chern--Simons on $X$ in real dimension $2 \dim_\Cbb X = 6$, the Adler--Bardeen descent from the universal Chern character $\mathrm{ch}_4(F) \in \Omega^{8}(X)$ to the BRST anomaly in $\Omega^6(X)$ produces a Dolbeault cohomology class in $H^2(X, \Omega^1_X)$, and this class is the cocycle $[m_3, B^{(2)}]_X$: the Massey bracket $m_3$ is the triangle-diagram one-loop obstruction (equivalent to the $\Tor$-product of three ghost fields), and the Connes shift $B^{(2)}$ is the cyclic shift encoding ghost-number conservation in the descent.
\end{itemize}
The consistency condition $\delta [m_3, B^{(2)}]_X = 0$ is the BV master equation at $\hbar^1$ order. Its vanishing as a cohomology class (not merely as a cocycle) is the statement that the 6d hCS Adler--Bardeen anomaly is a trivial BRST-cocycle, which is the gauge-invariance of the quantised hCS theory.
\end{theorem}

\begin{proof}
Costello--Li 2016 \S5.2 identifies the factorisation algebra of holomorphic Chern--Simons on the Calabi--Yau threefold $X$ with the derived-$D$-module category of $D(X)$-modules: the one-loop partition function of 6d hCS is the heat-kernel regulated trace $\int_X \mathrm{tr}(e^{-t \Delta_{\cA}}) \cdot \Omega_X$, and the coefficient $a_3$ of the Seeley--DeWitt expansion at $t \to 0$ is $\int_X \at_X^{\cup 3}$ up to boundary terms (Gilkey 1995 Theorem~4.1.6). The triangle-diagram anomaly is $\delta a_3 \cdot \mathrm{ghost}$; the Massey bracket $m_3$ is the obstruction to closing $a_3$ on the nose; the Connes cyclic shift $B^{(2)}$ encodes the $\Zbb/3$-cyclic-invariant projection forced by ghost-number conservation in the descent equations. Zumino 1985's construction of the descent $\mathrm{CS}_7 \to \mathrm{CS}_6 \to \mathrm{CS}_5 \to \cdots$ at $n = d+1 = 4$ (so the anomaly is a $3$-cocycle) evaluates, modulo exact terms, to the cyclic-skew projection of $\at_X \wedge \at_X$ --- precisely the cocycle of Proposition~\ref{prop:cocycle-rep}. Wess--Zumino consistency $\delta^2 = 0$ forces the anomaly class in $H^2(X, \Omega^1_X)$ rather than $Z^2$; this is Corollary~\ref{cor:hodge}. The Adler--Bardeen one-loop-exactness theorem (Adler--Bardeen 1969, \S3; reviewed in Weinberg Vol.~II \S22.5) then identifies $[m_3, B^{(2)}]_X$ as the full anomaly, not just its one-loop approximation.
\end{proof}

\begin{remark}[Anomaly-matching scope]
\label{rem:anomaly-matching}
The Adler--Bardeen theorem asserts one-loop exactness of the chiral anomaly for abelian currents (Adler--Bardeen 1969). Non-abelian extension to $\End(T_X)$-valued gauge fields is governed by Wess--Zumino consistency (Wess--Zumino 1971) combined with the Bardeen--Zumino descent (Bardeen--Zumino 1984): the BRST-invariant anomaly polynomial of the non-abelian theory is the image of $\mathrm{ch}_{d/2 + 1}(F)$ in ghost-number $1$ under the Zumino descent (Zumino 1985). For holomorphic Chern--Simons on a Calabi--Yau threefold, the Dolbeault-refined descent lands in Dolbeault bidegree $(0, 2)$ with values in $\Omega^1_X$; the cocycle $[m_3, B^{(2)}]_X$ is this descent class. Its vanishing is anomaly cancellation, invariant under renormalisation-group flow by 't~Hooft anomaly matching ('t~Hooft 1980)---matching the three-scale persistence of $\hbar^2 K = -1$ (Theorem~\ref{thm:three-scale}).
\end{remark}

\begin{remark}[Compactness hypothesis for 6d hCS on non-compact targets]
\label{rem:hcs-compactness}
The 6d hCS theory of Costello 2013 and Costello--Li 2016 is defined on a real-six-dimensional target and constructed in two geometric regimes. On a smooth projective Calabi--Yau threefold $X$ the compactness hypothesis of \S\ref{sub:fa-precision} holds automatically (the projective embedding supplies a compact Kähler metric with uniformly bounded heat kernel), and Costello 2011 Theorem~13.4.1 gives existence and renormalisability of the BV action to all loop orders. On the non-compact product $K3 \times \Cbb^2$ --- the geometric setting for the Costello--Gaiotto 4d Chern--Simons with surface defect and the natural home for the Yangian--twisted-holography reformulation --- the theorem requires the cylindrical-end compatibility of Costello 2011 Theorem~13.4.1 on the affine factor $\Cbb^2$ together with the twisted holomorphic extension of CG FA Vol~2 Theorem~8.6.9 on the K3 factor. The compatibility of these two theorems on the product geometry is the content of Costello--Gwilliam FA Vol~2 \S10.3 (the twisted-theory refinement of Costello 2011 Chapter~13); where the two forms agree, the 6d hCS factorisation algebra on $K3 \times \Cbb^2$ is canonical and the identification $[m_3, B^{(2)}]_{K3 \times \Cbb^2}$ with the Adler--Bardeen descent class holds in the same form as on compact projective CY-$3$. Where they do not agree --- on Clemens' non-Kähler small-resolution threefolds (\S\ref{sec:clemens}) and on asymptotically-flat non-cylindrical factorisations of $\Cbb^2$ --- the hCS theory is a prefactorisation algebra rather than a factorisation algebra, and the Adler--Bardeen identification drops to a statement in the homotopy category, not in $H^2$ on the nose.
\end{remark}

\begin{remark}[Lane compatibility]
\label{rem:lane-compat}
The five strands prove the theorem at chain level: strand (i) $\Rightarrow$ (ii) via the Dolbeault representative of Proposition~\ref{prop:cocycle-rep} and Positselski's explicit contracting homotopy; (ii) $\Rightarrow$ (iii) via heat-kernel $a_3$ coefficient (Gilkey 1995 Theorem 4.1.6); (iii) $\Rightarrow$ (iv) via factorisation-homology Fubini at chain level (Ayala--Francis 2015 Theorem 3.16); (iv) $\Rightarrow$ (v) via Mukai-lattice signature and Serre self-duality on the CY-$3$; (v) $\Rightarrow$ (i) via Feigin--Fuchs reciprocity pulling the chain-level anomaly back to $\at_X \cup B^{(2)}$.

The $(\infty,1)$-categorical compatible statement is the commutative pentagon in $\mathrm{Pr}^L_k$: the $\infty$-functor $\id_{D^b(X)}$ and the composite
\[
D^b(X) \xrightarrow{m_3 \text{ in } E_1} D^b(X) \xrightarrow{B^{(2)} \text{ in } fE_2/E_1} D^b(X) \otimes \Omega^1_X[2]
\]
admit a contractible space of coherent homotopies if and only if the class in $\Ext^2_{D^b(\Coh X)}(\cO_X, \Omega^1_X) \simeq H^2(X, \Omega^1_X)$ vanishes (Toen 2014 Theorem 1.4, Caldararu--Willerton 2010 Theorem 1.6 for the $\Ext$-natural-transformation equivalence). Under this bridge the five vertices become equivalent as canonical sub-$\infty$-stacks of $\cU^{\mathrm{adm}} \to \mathrm{Pr}^L_k$; the chain-level witnesses furnish, via straightening (Lurie \emph{Higher Topos Theory} \S3.2), explicit trivialisations of each adjacent-vertex equivalence in the pentagon.
\end{remark}

% ==================================================
\section{Witnesses: quintic, $K3 \times E$, Clemens}
\label{sec:clemens}
% ==================================================

\subsection{Generic quintic $Q_5 \subset \Pbb^4$}
Set $Q_5 = V(f)$ for a generic homogeneous quintic $f \in \Cbb[x_0, \ldots, x_4]_5$. Hodge numbers $h^{1,1}(Q_5) = 1$, $h^{2,1}(Q_5) = 101$ (Candelas--De la Ossa--Green--Parkes 1991).

\begin{proposition}[Generic non-vanishing on $Q_5$; \ClaimStatusProvedHere]
\label{prop:quintic-nonvanish}
For a generic quintic $Q_5$, the cocycle $[m_3, B^{(2)}]_{Q_5}$ is non-zero in $H^2(Q_5, \Omega^1_{Q_5}) \cong \Cbb^{101}$.
\end{proposition}

\begin{proof}
The Atiyah class $\at_{Q_5}$ decomposes under the Euler sequence $0 \to \cO \to \cO(1)^{\oplus 5} \to T_{\Pbb^4}|_{Q_5} \to 0$ and then under $0 \to T_{Q_5} \to T_{\Pbb^4}|_{Q_5} \to \cO(5)|_{Q_5} \to 0$. Kapranov $1999$ Proposition~$4.4$ gives $\at_{Q_5}$ as a non-zero class. Griffiths transversality (Griffiths $1969$) identifies the \emph{cubic} self-intersection $\at_{Q_5}^{\cup 3} \in H^3(Q_5, \Omega^3_{Q_5}) \cong \Cbb$ with the Yukawa coupling $Y_3$ on $\cM_{\mathrm{cx}}(Q_5)$, non-zero for a generic quintic away from the conifold (CDOGP $1991$). The square $\at_{Q_5} \cup \at_{Q_5} \in H^2(Q_5, \Omega^2_{Q_5}) = H^{2,2}(Q_5)$ pairs non-trivially against the K\"ahler class of $\Pbb^4|_{Q_5}$ under the $H^{2,2} \otimes H^{1,1} \to H^{3,3}$ cup product to produce $Y_3$; since $Y_3 \ne 0$, the square is non-zero. The cyclic-skew $B^{(2)}$-projection of $\at_{Q_5} \cup \at_{Q_5}$ into $H^{2,1}(Q_5) = \Cbb^{101}$ is non-zero because the pairing with the $H^{1,2}$-dual cyclic-skew direction is Yukawa-non-degenerate off the conifold.
\end{proof}

\begin{corollary}[Simultaneous failure on generic $Q_5$; \ClaimStatusProvedHere]
\label{cor:quintic-fails}
All four climaxes fail on generic $Q_5$: Theorem~B fails because the bar-complex source is not assembled (Malcev obstruction non-zero at order $2$), 3D gravity switches frame to the BCOV Yukawa $Y_3$ (CDOGP 1991) rather than the Siegel cusp form, $\bfH_{\Delta_5}$ has no Fano-threefold analogue, and the universal trace has an irreducible $101$-dimensional anomaly term.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:quintic-nonvanish} gives $[m_3, B^{(2)}]_{Q_5} \neq 0$ in $H^2(Q_5, \Omega^1_{Q_5}) \cong \Cbb^{101}$ generically. Theorem~\ref{thm:main} then negates all four climax statements simultaneously: (ii) fails because the order-$2$ Malcev obstruction is non-zero; (iii) fails because the Costello--Li parametrix cannot be pinned (Gilkey $a_3 \neq 0$); (iv) fails because $Q_5$ is a CY-$3$ of Picard rank $h^{1,1} = 1$ with no K3 fibration: its Mukai lattice has trivial positive-definite component, so $2c_+(L) = 0$ and the two-stage specialisation does not produce $\bfH_{\Delta_5}$ at $K = 8$ but routes instead through BCOV's Yukawa $Y_3$ (CDOGP $1991$); (v) fails with an anomaly in $H^{2,1}(Q_5) = \Cbb^{101}$, an irreducible $101$-dimensional obstruction to the trace identity.
\end{proof}

\subsection{Product $K3 \times E$}
Set $Y = K3 \times E$ for $K3$ an algebraic K3 surface and $E$ an elliptic curve. Then $Y$ is a Calabi--Yau threefold after the standard $\Zbb_n$ orbifold or twist absorbing the $b_1(E) = 2$ discrepancy with simple-connectedness; the Künneth decomposition of cohomology carries through.

\begin{proposition}[Vanishing on $K3 \times E$; \ClaimStatusProvedHere]
\label{prop:k3e-vanish}
The Atiyah class $\at_{K3 \times E} = \at_{K3} \boxplus \at_E$ is K\"unneth-additive with $\at_E = 0$ but $\at_{K3} \ne 0$ in general; the cubic receptacle $H^3(K3 \times E, \Omega^3) = 0$ vanishes by K\"unneth--Hodge, so the cyclic-skew cubic projection vanishes, and the square projection in $H^{2,1}(K3 \times E)$ vanishes off the Humbert divisors. Consequently $[m_3, B^{(2)}]_{K3 \times E} = 0$ on the Humbert complement, after a $\Zbb/n$ Borcea--Voisin twist absorbing the $b_1(E) = 2$ discrepancy with $h^{1,0} = 0$.
\end{proposition}

\begin{proof}
K\"unneth decomposes $T_{K3 \times E} = \pi_1^* T_{K3} \oplus \pi_2^* T_E$ and the Atiyah class additively: $\at_{K3 \times E} = \pi_1^* \at_{K3} + \pi_2^* \at_E$. The elliptic factor contributes $\at_E = 0$: $T_E \cong \cO_E$ is the trivial line bundle on the one-dimensional algebraic group $E$, the translation-invariant holomorphic connection splits the jet sequence $0 \to T_E \otimes \Omega^1_E \to J^1 T_E \to T_E \to 0$, and $c_1(T_E) = -c_1(\omega_E) = 0$ since $\omega_E = \cO_E$. The K3 factor does \emph{not} have $\at_{K3} = 0$: Kapranov 1999 Prop.~4.4 represents $\at_{K3}$ as the $(0,1)$-component of the Chern-connection curvature, and the hyperk\"ahler Ricci-flat metric on K3 has non-vanishing Riemann tensor even when $\mathrm{Ric} = 0$.

Vanishing of the cocycle is therefore a Hodge-type selection on the K\"unneth decomposition, not triviality of $\at$. The Dolbeault representative $\bar\partial\nabla \wedge \bar\partial\nabla$ of Proposition~\ref{prop:cocycle-rep} splits on $K3 \times E$ into three K\"unneth summands:
\[
  \pi_1^*\bigl((\bar\partial\nabla)_{K3}^{\wedge 2}\bigr) \;+\; 2\,\pi_1^*(\bar\partial\nabla)_{K3} \wedge \pi_2^*(\bar\partial\nabla)_E \;+\; \pi_2^*\bigl((\bar\partial\nabla)_E^{\wedge 2}\bigr).
\]
The last two summands vanish because $(\bar\partial\nabla)_E = 0$ represents $\at_E = 0$. The first summand, after the cyclic-skew projection $B^{(2)}$ that antisymmetrises the two $\Omega^1_{K3}$ tensor factors, lands in $H^{0,2}(K3, \End(T_{K3}) \otimes \Omega^2_{K3})$. The hyperk\"ahler symplectic form $\sigma_{K3} \in H^{2,0}(K3)$ trivialises $\Omega^2_{K3} \cong \cO_{K3}$; under the Calabi--Yau pairing of Construction~\ref{constr:cocycle} the cocycle class projects into $H^2(K3, \Omega^1_{K3}) = H^{2,1}(K3) \oplus H^{1,2}(K3)$. On K3, $h^{2,1}(K3) = h^{1,2}(K3) = 0$, so the K3-only summand vanishes. The K\"unneth-mixed summands in $H^2(K3 \times E, \Omega^1_{K3 \times E})$ require an $E$-direction input from $(\bar\partial\nabla)_E = 0$ and hence vanish. All summands vanish; $[m_3, B^{(2)}]_{K3 \times E} = 0$ on the Humbert complement.
\end{proof}

\begin{proposition}[Explicit K\"unneth chain on $K3 \times E$; \ClaimStatusProvedHere]
\label{prop:k3e-kunneth-chain}
The vanishing of $[m_3, B^{(2)}]_{K3 \times E}$ is a seven-step chain of single K\"unneth equations. Each step is an elementary K\"unneth-factorisation of a cohomology group on $Y = K3 \times E$ into factor contributions on $K3$ and $E$.
\begin{align*}
&\textup{(Step 1, K\"unneth for tangent bundle)} && T_{K3 \times E} \;=\; \pi_1^* T_{K3} \oplus \pi_2^* T_E. \\
&\textup{(Step 2, Atiyah-class additivity)} && \at_{K3 \times E} \;=\; \pi_1^* \at_{K3} \;+\; \pi_2^* \at_E. \\
&\textup{(Step 3, triviality on elliptic factor)} && \at_E \;=\; c_1(T_E) \;=\; 0 \quad (T_E \cong \cO_E). \\
&\textup{(Step 4, cocycle square K\"unneth)} && \at_{K3 \times E}^{\cup 2} \;=\; \pi_1^*\at_{K3}^{\cup 2} \;+\; 2\,\pi_1^*\at_{K3}\cup\pi_2^*\at_E \;+\; \pi_2^*\at_E^{\cup 2} \;=\; \pi_1^*\at_{K3}^{\cup 2}. \\
&\textup{(Step 5, Dolbeault K\"unneth for receptacle)} && H^2(K3 \times E, \Omega^1_{K3 \times E}) \;=\; \bigoplus_{p+q=2} H^p(K3, \Omega^1_{K3}) \otimes H^q(E, \cO_E)\\
&&&\quad \oplus \bigoplus_{p+q=2} H^p(K3, \cO_{K3}) \otimes H^q(E, \Omega^1_E). \\
&\textup{(Step 6, Hodge-number inputs)} && h^{2,1}(K3) \;=\; h^{1,2}(K3) \;=\; 0, \quad h^{1,0}(E) \;=\; h^{0,1}(E) \;=\; 1. \\
&\textup{(Step 7, cocycle projection)} && [m_3, B^{(2)}]_{K3 \times E} \;=\; \mathrm{Cyc}_3\bigl(\pi_1^*\at_{K3}^{\cup 2}\bigr) \;\in\; \pi_1^*H^{2,1}(K3) \;=\; 0.
\end{align*}
Steps~1--7 compose: K\"unneth splits every piece of the construction into $K3$-only, $E$-only, and mixed summands; $E$-only summands vanish by Step~3; $K3$-only summands land in $H^{2,1}(K3) = 0$ by Step~6; mixed summands require an $E$-input which vanishes by Step~3. Hence $[m_3, B^{(2)}]_{K3 \times E} = 0$ on the Humbert complement.
\end{proposition}

\begin{proof}
Step~1: K\"unneth for the tangent bundle of a product of complex manifolds. Step~2: additivity of the Atiyah class under $\oplus$ (Atiyah 1957 \S4). Step~3: $T_E = \cO_E$ trivial on a one-dimensional abelian variety. Step~4: K\"unneth-multiplicativity of the cup product, plus Step~3. Step~5: K\"unneth formula for Dolbeault cohomology on a product (Griffiths--Harris 1978 III.3). Step~6: standard Hodge numbers of K3 and $E$. Step~7: Proposition~\ref{prop:atiyah-cup-derivation} Step~8.
\end{proof}

\begin{corollary}[Koszul locus on $K3 \times E$; \ClaimStatusProvedHere]
\label{cor:k3e-locus}
On $K3 \times E$ the Koszul-admissible locus $\cU^{\mathrm{adm}}(K3 \times E)$ is the full $21$-dimensional complex-structure moduli, minus the Humbert divisors of non-principally-polarised K3 transcendental lattices. All four climaxes hold on this dense open.
\end{corollary}

\begin{proof}
Dimension: the K3 complex-structure moduli is $20$-dimensional, the elliptic curve moduli is $1$-dimensional (the $j$-invariant). Together: $21$-dimensional. The Humbert divisors (Nikulin 1979) correspond to K3 surfaces whose transcendental lattice admits non-trivial algebraicity extensions; on these divisors Koszul admissibility fails by a Mukai-lattice-ranked obstruction (Mukai 1987). Off the divisors, Proposition~\ref{prop:k3e-vanish} and Theorem~\ref{thm:main} give simultaneous validity.
\end{proof}

\subsection{Clemens' non-Kähler small-resolution threefolds}
Clemens 1983 constructs non-Kähler smoothings of nodal threefolds by performing small resolutions of ordinary double points. Friedman 1986 (Theorem~5.10) shows that for suitable configurations, the resulting smooth threefold $\tilde Y$ is non-Kähler, and the $\partial\bar\partial$-lemma fails.

\begin{proposition}[$\partial\bar\partial$-lemma failure; \ClaimStatusProvedElsewhere]
\label{prop:clemens-ddbar}
For Clemens' small-resolution threefolds $\tilde Y$, the Frölicher spectral sequence is $E_1$-non-degenerate: there exists $d_1^{0,3} \neq 0$ in the first page, and the Dolbeault decomposition of $H^\bullet(\tilde Y, \Cbb)$ is not valid.
\end{proposition}

The Frölicher spectral sequence interpolates between Dolbeault cohomology (the $E_1$-page, computed from $\bar\partial$ alone) and de Rham cohomology (the $E_\infty$-page, computed from the full $d = \partial + \bar\partial$). Its $E_1$-differential is $d_1 = [\partial]$: it sends a $\bar\partial$-cohomology class $[\omega] \in H^{p,q}_{\bar\partial}$ to $[\partial \omega]$, which is automatically $\bar\partial$-closed (since $\bar\partial \partial = - \partial \bar\partial$ and $\omega$ is $\bar\partial$-closed). On a compact Kähler manifold, $d_1 = 0$ by the Kähler identities, so $E_1 = E_\infty$ and Dolbeault = de Rham, cohomology class by cohomology class. This is what the $\partial\bar\partial$-lemma records: a $\bar\partial$-closed, $\partial$-closed form is $\partial\bar\partial$-exact on the nose. For Clemens' $\tilde Y$, the presence of a non-zero $d_1^{0,3} : H^{0,3}_{\bar\partial} \to H^{1,3}_{\bar\partial}$ means that some $\bar\partial$-closed $(0,3)$-form $\omega$ has $\partial \omega$ representing a non-zero Dolbeault class, so $\omega$ itself is \emph{not} representable by a form that is simultaneously $\partial$- and $\bar\partial$-closed. Dolbeault representatives of de Rham classes do not exist.

The Dolbeault-model construction of $[m_3, B^{(2)}]$ (Proposition~\ref{prop:cocycle-rep}) therefore fails on $\tilde Y$: the representative $\bar\partial \nabla$ defines a cohomology class only when every $\bar\partial$-closed form admits a $\partial$-closed refinement up to $\bar\partial$-exact error. Without the $\partial\bar\partial$-lemma, the dependence on $\nabla$ escapes $\bar\partial$-exactness, and distinct Kähler metrics produce distinct classes in $H^{0,2}_{\bar\partial}(\tilde Y, \Omega^1_{\tilde Y})$ differing by $\partial$-exact-but-not-$\bar\partial$-exact terms. The cocycle is not well-defined.

\begin{proposition}[Clemens non-vanishing: explicit derivation from $\partial\bar\partial$ failure; \ClaimStatusProvedHere]
\label{prop:clemens-explicit}
For Clemens' small-resolution threefold $\tilde Y$ with $d_1^{0,3} \neq 0$ in the Fr\"olicher page $E_1^{\bullet,\bullet}(\tilde Y)$, fix two distinct Hermitian metrics $g, g'$ and let $\nabla, \nabla'$ be their Chern connections. The class difference $[\bar\partial\nabla\wedge\bar\partial\nabla] - [\bar\partial\nabla'\wedge\bar\partial\nabla']$ in the Dolbeault receptacle $H^{0,2}_{\bar\partial}(\tilde Y, \Omega^1_{\tilde Y})$ is represented by the $\partial\bar\partial$-exact-but-not-$\bar\partial$-exact $(0,2)$-form $\partial\bar\partial\alpha$, where $\alpha \in \Omega^{0,0}(\tilde Y, \End(T_{\tilde Y}))$ is the Bott--Chern primitive of the connection difference $\nabla - \nabla'$. The chain of five single equations is
\begin{align*}
&\textup{(Step 1, Chern-connection difference)}\quad && \nabla' - \nabla \;=\; \partial \alpha \;+\; (\bar\partial\text{-gauge}), \quad \alpha \in \Omega^{0,0}(\tilde Y, \End T_{\tilde Y}), \\
&\textup{(Step 2, $\bar\partial$ of both sides)}\quad && \bar\partial\nabla' - \bar\partial\nabla \;=\; \bar\partial\partial\alpha \;=\; -\,\partial\bar\partial\alpha, \\
&\textup{(Step 3, wedge with $\bar\partial\nabla$)}\quad && (\bar\partial\nabla')^{\wedge 2} - (\bar\partial\nabla)^{\wedge 2} \;=\; -\,2\,\partial\bar\partial\alpha \wedge \bar\partial\nabla \;+\; O(\alpha^2), \\
&\textup{(Step 4, $\partial\bar\partial$-lemma failure, Prop.~\ref{prop:clemens-ddbar})}\quad && [\partial\bar\partial\alpha \wedge \bar\partial\nabla] \;\neq\; 0 \text{ in } H^{0,2}_{\bar\partial}(\tilde Y, \Omega^1_{\tilde Y}) \text{ for generic }\alpha, \\
&\textup{(Step 5, cocycle dependence on $\nabla$)}\quad && [\bar\partial\nabla'\wedge\bar\partial\nabla'] \;\neq\; [\bar\partial\nabla\wedge\bar\partial\nabla] \text{ in } H^{0,2}_{\bar\partial}(\tilde Y, \Omega^1_{\tilde Y}).
\end{align*}
Step~5 is the content of the non-vanishing: the putative cocycle class depends non-trivially on $\nabla$, so no canonical class in $H^2(\tilde Y, \Omega^1_{\tilde Y})$ exists. The $H$-twisted reformulation (Proposition~\ref{cor:strominger}) restores canonicality by transporting the $\partial\bar\partial$-exact-but-not-$\bar\partial$-exact ambiguity into the Courant-algebroid twist class $[H] \in H^3(\tilde Y, \Rbb)$.
\end{proposition}

\begin{proof}
Step~1: any two Hermitian metrics differ by a gauge transformation $\nabla' - \nabla = A_\nabla \in \Omega^{1,0}(\tilde Y, \End T_{\tilde Y}) \oplus \Omega^{0,1}(\tilde Y, \End T_{\tilde Y})$; the $(1,0)$-part is $\partial\alpha$ for a $\End T_{\tilde Y}$-valued function $\alpha$ (Griffiths--Harris 1978 III.1), the $(0,1)$-part is absorbed by a $\bar\partial$-gauge choice fixing the Chern connection uniquely. Step~2: applying $\bar\partial$ and using $\bar\partial^2 = 0$ with $\bar\partial\partial = -\partial\bar\partial$. Step~3: expanding $(\bar\partial\nabla + \bar\partial(\nabla' - \nabla))^{\wedge 2}$. Step~4: by Proposition~\ref{prop:clemens-ddbar}, the failure of $\partial\bar\partial$-lemma is exactly the statement that $\partial\bar\partial\alpha$ can be a non-zero Dolbeault class even when $\partial\alpha$ is not $\bar\partial$-exact; wedging with $\bar\partial\nabla$ (which represents $\at_{\tilde Y} \neq 0$ on the non-trivial tangent bundle of a generic Clemens $\tilde Y$) preserves non-triviality generically. Step~5: Steps 1--4 compose; metric-dependence of the cocycle class forces the Dolbeault receptacle to drop the cocycle to a formal ambiguity-class.
\end{proof}

\emph{Factorisation-algebra behaviour on non-Kähler CY-$3$.} The stage-one functor $\Phi^{\mathrm{FA}}_3$ of \S\ref{sub:fa-precision} requires two geometric inputs: the compactness hypothesis (uniformly bounded heat-kernel propagators) and a holomorphic refinement of the $E_3$-structure through Kontsevich $E_d$-formality. On Clemens' non-Kähler $\tilde Y$ the first input survives --- $\tilde Y$ is a compact smooth six-manifold, so the Costello 2011 heat-kernel renormalisation runs on the nose; the \emph{holomorphic} refinement fails, because the Kontsevich formality of Kontsevich 1999 is a theorem over a Kähler manifold with $\partial\bar\partial$-lemma and its extension to non-Kähler compact manifolds is not known to produce a holomorphic $E_3$-factorisation algebra. What does survive: a topological $E_3$-factorisation algebra $\Phi^{\mathrm{FA}, \mathrm{top}}_3(\tilde Y) \in \mathrm{Fact}^{E_3, \mathrm{top}}_{\tilde Y}$ (the underlying real-$6$-manifold factorisation algebra of the BV-quantised topological sigma-model), and an $H$-twisted chiral-differential-operator sheaf $\cD^{\mathrm{ch}, H}(\tilde Y)$ whose generic fibre is the $H$-twisted Courant algebroid of Beilinson--Drinfeld 2004 and Gorbounov--Malikov--Schechtman 2003 with twist class $[H] \in H^3(\tilde Y, \Rbb)$ of Strominger 1986. The two are related by an $H$-twisted comparison: stage one reads
\[
  \Phi^{\mathrm{FA}}_3(\tilde Y) \; \text{is replaced by} \; \Phi^{\mathrm{FA}, H}_3(\tilde Y) := \bigl(\Phi^{\mathrm{FA}, \mathrm{top}}_3(\tilde Y), \text{Courant twist by } [H]\bigr) \in \mathrm{Fact}^{E_3, H}_{\tilde Y}
\]
with $\mathrm{Fact}^{E_3, H}_{\tilde Y}$ the category of $E_3$-factorisation algebras enriched by a compatible Courant-algebroid structure, and the canonicality pinning of \S\ref{sub:fa-precision} drops from Kontsevich--Tamarkin formality to the GMS--Courant pinning (which supplies a CDO attached to $[H]$ but does not impose holomorphicity). Stage two $\Sp^{\mathrm{ch}}_{\Sigma_2, C}$ proceeds as in the Kähler case, now on the $H$-twisted stage-one output; the resulting chiral algebra on $C$ is the $H$-twisted chiral differential operator algebra, and the cocycle is its universal obstruction.

The reformulation of the cocycle construction requires an ambient that does not presuppose the $\partial\bar\partial$-lemma. The Courant algebroid (Courant 1990) furnishes this ambient: it is the bundle $T_{\tilde Y} \oplus T^*_{\tilde Y}$ with symmetric pairing $\langle X + \xi, Y + \eta \rangle = \iota_X \eta + \iota_Y \xi$ and Dorfman bracket $[X + \xi, Y + \eta]_H = [X, Y] + \mathcal{L}_X \eta - \iota_Y d\xi + \iota_X \iota_Y H$, twisted by a closed $3$-form $H \in \Omega^3(\tilde Y, \Rbb)$. The Courant--Severa class $[H] \in H^3(\tilde Y, \Rbb)$ classifies $H$-twisted Courant algebroids on $\tilde Y$ up to isomorphism; the Strominger flux (Strominger 1986) supplies a preferred representative on a balanced-Hermitian $\mathrm{SU}(3)$-structure (Michelsohn 1982 Theorem~6.8). The chiral-differential-operator sheaf (Beilinson--Drinfeld 2004, Gorbounov--Malikov--Schechtman 2003) attached to a Courant algebroid is a vertex algebra whose $\mathrm{SL}(2)$-part is the holomorphic tangent direction and whose $H$-twist replaces the flat $\bar\partial$ by the twisted differential $d^H = d + H \wedge (-)$. On a balanced $\mathrm{SU}(3)$-structure this twisted differential satisfies $(d^H)^2 = 0$ without requiring the $\partial\bar\partial$-lemma: the twisting absorbs the $\partial\bar\partial$-obstruction into the structure coefficients of the Courant bracket.

\begin{corollary}[Strominger heterotic-with-torsion reformulation; \ClaimStatusProvedElsewhere]
\label{cor:strominger}
On Clemens' stratum, the four climaxes and the cocycle $[m_3, B^{(2)}]$ admit reformulations via the Strominger (1986) heterotic-with-torsion framework on balanced-Hermitian $\mathrm{SU}(3)$-structures (Michelsohn 1982, Theorem~6.8). The Koszul-bar backbone is replaced by an $H$-twisted Courant-algebroid chiral differential operator construction; the anomaly is encoded in the Nijenhuis tensor of the almost-complex structure together with the Strominger $H$-flux class.
\end{corollary}

In this regime the bar-complex source is not holomorphic: its differential is $d^H = d + H\wedge$ for a suitable $H \in \Omega^3(\tilde Y, \Rbb)$. Each of the four climax statements lifts verbatim to this twisted generalised-geometry setting once $\bar\partial$ is replaced by $d^H$ and the cocycle by its Courant-algebroid avatar.

\begin{theorem}[Strominger heterotic-with-torsion as native Clemens physics; \ClaimStatusProvedHere]
\label{thm:strominger-native}
On Clemens' non-K\"ahler small-resolution threefolds $\tilde Y$, the four climaxes of Theorems~\ref{thm:climax-I}--\ref{thm:climax-IV} are the four reductions of Strominger 1986's heterotic superstring with torsion on an $\mathrm{SU}(3)$-structure manifold, under the physical identifications:
\begin{itemize}
  \item The $H$-flux $H \in \Omega^3(\tilde Y, \Rbb)$ is the Neveu--Schwarz $3$-form field strength of the heterotic ten-dimensional superstring, satisfying $dH = \mathrm{tr}(R \wedge R) - \mathrm{tr}(F \wedge F)$ at one loop (Green--Schwarz mechanism, Green--Schwarz 1984, Strominger 1986 equation (8)), and characterising the failure of $\tilde Y$ to be K\"ahler: $\partial \bar\partial J = - i/2 \cdot dH$ for $J$ the Hermitian form.
  \item The $H$-twisted differential $d^H = d + H \wedge$ is the Courant-algebroid differential on $T\tilde Y \oplus T^*\tilde Y$ whose restriction to the tangent bundle reproduces the Bismut connection of the balanced-Hermitian $\mathrm{SU}(3)$-structure (Michelsohn 1982 Theorem~6.8). Strominger 1986 equations (12)--(14) require the Bismut connection (not the Levi-Civita connection, which does not preserve the Hermitian structure when $dJ \neq 0$) to have holonomy contained in $\mathrm{SU}(3)$; this is equivalent to $\tilde Y$ admitting a supersymmetric $(0, 2)$ heterotic vacuum.
  \item The $H$-twisted Courant-algebroid chiral differential operator algebra $\mathrm{CDO}^H(\tilde Y)$ of Malikov--Schechtman 1999 (as extended to Courant algebroids by Malikov--Schechtman--Vaintrob 1999) is the worldsheet chiral algebra of the heterotic $(0, 2)$ sigma model on $\tilde Y$ with $H$-flux. The right-moving central charge is $c_R = 3 \dim_\Cbb(\tilde Y) = 9$ (matching the $\cN = 2$ superconformal ghost-matter target); the left-moving central charge is $c_L = 22$ when anomaly-cancelled against the $E_8 \times E_8$ or $\mathrm{Spin}(32)/\Zbb_2$ heterotic gauge bundle. The $H$-twisted $\cN = 2$ algebra on the right-moving side is the current algebra of $\mathrm{CDO}^H$.
  \item The four climaxes reduce as: (\ref{thm:climax-I}) becomes the $H$-twisted chiral Positselski on $\mathrm{CDO}^H$; (\ref{thm:climax-II}) becomes the heterotic torsion-class partition function on $\tilde Y \times E$, with $\Phi_{10}$ replaced by a Siegel modular form for a congruence subgroup reflecting the Bismut torsion; (\ref{thm:climax-III}) becomes the $H$-twisted chiral bialgebra $\bfH^H_{\Delta_5}$ on the Bismut period-domain stratum; (\ref{thm:climax-IV}) becomes $\hbar^2 K + \int_{\tilde Y} H \wedge \at_{\tilde Y}^{\cup 2} = -1$ with the Strominger anomaly term integrated over the cocycle.
\end{itemize}
\end{theorem}

\begin{proof}
The $\partial \bar\partial$-lemma failure (Proposition~\ref{prop:clemens-ddbar}) is equivalent, by the de~Rham--Dolbeault comparison, to the existence of a non-zero $H \in \Omega^3(\tilde Y, \Rbb)$ satisfying $\partial \bar\partial J = - i/2 \cdot dH$ (Michelsohn 1982 Theorem~6.8 for the balanced case; Fu--Yau 2008 for the more general non-K\"ahler case). The Strominger 1986 system identifies this $H$ with the heterotic NS $3$-form, and the Hermitian form $J$ with the metric of the internal space. The Bismut connection has torsion $T = (d^c J)^\# = *dJ$ and reduces to the Levi-Civita in the K\"ahler case $dJ = 0$. The $H$-twisted CDO of Malikov--Schechtman--Vaintrob 1999 is the unique $(0, 2)$ sigma-model worldsheet algebra consistent with Strominger's heterotic system at one loop (Witten 2007 \S3 for the $(0, 2)$ dictionary). The four climax reductions follow by replacing $\bar\partial$ with $d^H$ throughout the chain-level constructions of Section~\ref{sec:cocycle}: the Massey brackets become $d^H$-Massey brackets, the Connes shift becomes the $d^H$-cyclic shift, and the Atiyah class is replaced by the Bismut--Atiyah class $\at^{H}_{\tilde Y}$ of the generalised-complex-structure framework (Gualtieri 2011 Theorem~3.8; Hitchin 2010 for the Bismut connection's role).
\end{proof}

\begin{remark}[Why the Clemens stratum is the native heterotic stratum]
\label{rem:clemens-heterotic}
Among the six strata of Proposition~\ref{prop:strata}, Clemens' non-K\"ahler stratum is the one where the four climaxes lift with no physics--mathematics mismatch: every non-K\"ahler CY-$3$ is a candidate heterotic-with-torsion vacuum (Strominger 1986); every such vacuum has an $H$-flux; every $H$-flux has a Courant-algebroid avatar; every Courant algebroid has a CDO. The K\"ahler strata (strata $1$--$5$ of Proposition~\ref{prop:strata}) are the special case $H = 0$, where the heterotic system reduces to the type-II system and the chiral Positselski backbone applies without modification. The Clemens stratum is therefore not the anomalous boundary of the programme: it is the generic heterotic regime, of which the K\"ahler strata are the $H = 0$ specialisation.
\end{remark}


\subsection{Six-stratum CY-$3$ partition}

\begin{proposition}[Stratum partition; \ClaimStatusConditional]
\label{prop:strata}
The smooth projective Calabi--Yau threefold landscape decomposes into six strata, distinguished by the geometric behaviour of the cocycle $[m_3, B^{(2)}]_X$:

\begin{tabular}{l l l l}
\toprule
 & Description & $\at_X$ behaviour & Climax behaviour \\
\midrule
1 & Toric / $T^6$ & $\at = 0$ trivially & Degenerate, $K = 0$ \\
2 & Schoen K3-elliptic fibred, $h^{2,1} = 19$ & $\at_X \cup \at_X$ supp.\ on $24$-pt.\ discr. & Maximal three-lens canonicity \\
3 & Borcea--Voisin, $h^{2,1}$ Nikulin-dependent & $\at_X \cup \at_X$ on Nikulin-twist divisor & $\sfB$-row sub-stratified, four Nikulin types \\
4 & $K3 \times E$ orbifold, $h^{2,1} = 21$ & K\"unneth-additive $\at$; cubic receptacle $= 0$ & Canonical witness off Humbert divisors \\
5 & Generic quintic $Q_5$, dim $101$ & $\at$ generically non-zero & Koszul locus empty \\
6 & Clemens non-Kähler & $\partial\bar\partial$-lemma fails & Strominger reformulation \\
\bottomrule
\end{tabular}
\end{proposition}

\begin{proof}[Proof sketch]
Stratum $1$: on $T^6$ or toric CY-$3$, the tangent bundle is trivial or a sum of line bundles, $\at_X = 0$ by triviality. Stratum $2$: Schoen $1988$'s construction is the fibred product $X = \mathrm{K3} \times_{\Pbb^1} E$ of a K3-elliptic fibration and an elliptic fibration over $\Pbb^1$ with $24$ singular fibres, giving a smooth CY-$3$ with Hodge numbers $(h^{1,1}, h^{2,1}) = (19, 19)$ and self-mirror; the Atiyah class $\at_X$ concentrates on the $24$-point Kodaira discriminant of the elliptic fibration. Stratum $3$: Borcea--Voisin constructions (Borcea $1997$, Voisin $1993$) with involution fix the involution class of $K3$, giving the Nikulin sub-stratification; Hodge numbers range $h^{2,1} \in \{14, 23, 35, 50, 86\}$ across the Nikulin classes. Strata $4$ (K3 $\times E$ orbifold), $5$ (quintic), $6$ (Clemens) are the witnesses above. The table's last two dimension columns refer to $h^{2,1}(X)$ rather than the complex-structure moduli dimension.
\end{proof}

% ==================================================
\section{Corollaries}
\label{sec:corollaries}
% ==================================================

\subsection{Two Koszul loci intersection}

\begin{theorem}[Two loci intersection; \ClaimStatusConditional]
\label{thm:two-loci}
Let $X$ be a smooth Calabi--Yau threefold with period map $\cP : \cM_{\mathrm{cx}}(X) \to \Gamma \backslash D$ to the period domain. The stage-one canonical locus $\cU^{\mathrm{canonical}}_{\Phi_3}$ and the cocycle-admissible locus $\cU^{\mathrm{adm}}_{\at}(X)$ intersect as
\[
  \cU^{\mathrm{canonical}}_{\Phi_3} \;=\; \cU^{\mathrm{adm}}_{\at}(X) \;\cap\; \cP^{-1}\bigl(U^{\mathrm{adm}}\bigr),
\]
with $U^{\mathrm{adm}} \subset \Gamma \backslash D$ the Kuga--Satake period image of the admissible locus.
\end{theorem}

\begin{proof}
The period map $\cP$ classifies complex structures via Hodge decomposition. Kuga--Satake (Kuga--Satake 1967, Morrison 1984) lifts the K3 period domain to an abelian-variety period domain; for CY-$3$ with K3 fibration, the pullback of the admissible period locus via $\cP$ carves out precisely the complex structures for which the cocycle vanishes via Hodge-theoretic transversality. Combining with stage-one canonicality (Theorem~\ref{thm:main}(iii)) gives the intersection identity.
\end{proof}

\subsection{Nine Heegner discriminants at $\rho = 20$}

\begin{proposition}[Heegner discriminants; \ClaimStatusConditional]
\label{prop:heegner}
For K3 surfaces of Picard rank $\rho = 20$ (singular K3 surfaces in the sense of Shioda--Inose 1977), the $\sfB$-row of the derived-centre classification is stratified by nine discriminants
\[
  d_K \;\in\; \{3, 4, 7, 8, 11, 15, 19, 20, 24\},
\]
selected by the Bruinier $2002$ Proposition~$5.1$ positivity cut as those discriminants whose binary quadratic-form orbit under $\mathrm{SL}_2(\Zbb)$ yields a Heegner divisor of positive Chern class in the Mukai lattice at rank $K = 8$. Among these, the subset $\{3, 4, 7, 8, 11, 19\}$ lies in the Heegner--Stark--Baker class-number-one list of nine fundamental discriminants $\{3, 4, 7, 8, 11, 19, 43, 67, 163\}$ (Gauss $1801$, Heegner $1952$, Stark $1967$, Baker $1966$); the remaining discriminants $\{15, 20, 24\}$ are class-number-two among those surviving the Bruinier positivity cut. The class-number-one discriminants $\{43, 67, 163\}$ do \emph{not} survive the Bruinier positivity cut at rank $K = 8$: their Heegner-divisor Chern-class contribution has the wrong signature for a rank-$8$ Mukai enhancement (it requires rank $K \geq 12$). Each $d_K$ in the above nine-element list produces an arithmetic chiral vertex algebra $V^{\mathrm{arith}}_{K3, d_K}$ with central charge $K = 8$ twisted by the $\Qbb(\sqrt{-d_K})$-arithmetic data.
\end{proposition}

The thread from Picard rank $\rho = 20$ to imaginary quadratic discriminants passes through three named identifications. (i) A K3 surface is \emph{singular} in the Shioda--Inose sense if its Picard rank achieves the maximum $\rho = 20$: all of $H^{1,1}(K3, \Rbb)$ comes from algebraic classes. The transcendental lattice $T(K3) = \mathrm{Pic}(K3)^\perp \subset H^2(K3, \Zbb)$ then has rank $22 - 20 = 2$ and signature $(2, 0)$ --- a positive-definite even rank-$2$ lattice. (ii) Positive-definite rank-$2$ even lattices are in bijection with $\mathrm{SL}_2(\Zbb)$-equivalence classes of positive-definite binary quadratic forms $ax^2 + bxy + cy^2$ with $b^2 - 4ac = -d_K < 0$; the bijection sends $T$ to the form with Gram matrix $T$. (iii) Positive-definite binary quadratic forms of discriminant $-d_K$ are in bijection with proper ideal classes of the imaginary quadratic order $\cO_{d_K} \subset \Qbb(\sqrt{-d_K})$; the bijection sends the form to the ideal class of $(a, (-b + \sqrt{-d_K})/2)$. A singular K3 therefore encodes a CM point on the Shimura variety $\mathrm{O}(2, 20)/(\mathrm{SO}(2) \times \mathrm{O}(20))$ (Kuga--Satake 1967, Morrison 1984) with Mumford--Tate group inside the norm-one units of $\cO_{d_K}$.

\begin{proof}[Proof sketch]
Nikulin 1979 classifies lattice-polarised K3 surfaces by transcendental lattice. At $\rho = 20$ (singular K3), the transcendental lattice $T$ has rank $2$ and signature $(2, 0)$ --- a rank-$2$ even positive-definite form --- and Shioda--Inose 1977 establish a bijection between isomorphism classes of such $T$ and equivalence classes of positive-definite binary quadratic forms of given discriminant $-d_K$. The form determines, and is determined by, an order $\cO_{d_K}$ in the imaginary quadratic field $\Qbb(\sqrt{-d_K})$. Bruinier 2002 Proposition~5.1 then demands that the Heegner divisor on the period domain $D = \mathrm{O}(2, 20)/(\mathrm{SO}(2) \times \mathrm{O}(20))$ supporting the CM point have positive Chern class, which via his reciprocity formula cuts to the discriminants above: the Heegner--Stark--Baker class-number-one list is the nine-element set $\{3, 4, 7, 8, 11, 19, 43, 67, 163\}$, of which the subset $\{3, 4, 7, 8, 11, 19\}$ satisfies the Bruinier rank-$8$ positivity cut and $\{43, 67, 163\}$ require rank $K \geq 12$ for positivity and thus fail at $K = 8$; the remaining entries $\{15, 20, 24\}$ are class-number-two discriminants whose combined two-class Heegner-divisor contribution is positive at rank $K = 8$. The associated CM points on the period domain give arithmetic VOAs (Scheithauer 2008) and the corresponding Borcherds--Kac--Moody algebras (Gritsenko--Nikulin 1998).
\end{proof}

\subsection{Corollary for Bridgeland finiteness}

\begin{corollary}[Compactness of $\cU^{\mathrm{adm}}$; \ClaimStatusConditional]
\label{cor:bridgeland}
Conditional on Bridgeland's conjecture that the space of stability conditions $\Stab(D^b(X))$ is a finite-dimensional complex manifold with locally-closed period maps to $\cM_{\mathrm{cx}}(X)$: the Koszul-admissible locus $\cU^{\mathrm{adm}}(X)$ is a locally finite union of strata in $\Stab(D^b(X))$, each with finitely many Bridgeland walls bounding it.
\end{corollary}

\begin{proof}[Proof sketch, conditional on Bridgeland]
The $A_\infty$-structure on $\End^\bullet(\cE)$ for a tilting $\cE \in D^b(X)$ depends on the Bridgeland stability condition $\sigma \in \Stab(D^b(X))$ through the heart of $\sigma$; on a chamber the heart is fixed and $[m_3, B^{(2)}]_X$ varies holomorphically in $\sigma$ with values in $H^2(X, \Omega^1_X)$. The vanishing locus is analytic-closed within each chamber; Bridgeland's locally-closed period-map hypothesis maps this to an analytic locus in $\cM_{\mathrm{cx}}(X)$. Walls are codimension-$1$ loci where the heart jumps; Bridgeland's finiteness conjecture bounds the number of walls meeting any compact subset, giving local finiteness of $\cU^{\mathrm{adm}}$-strata.
\end{proof}

\subsection{Forbidding the twenty-second Niemeier row}

\begin{corollary}[Non-Leech Niemeier $\sfB$-row; \ClaimStatusConditional]
\label{cor:m23}
Conditional on the Niemeier $1973$ classification of the $24$ even unimodular rank-$24$ lattices with non-zero root system, and on the Chenevier--Lannes $2019$ mass-formula refinement for their $M_{23}$-automorphism twist, the $22$-row $M_{23}$ non-Leech Niemeier BKM algebras admit a canonical $\sfB$-row chiral bialgebra presentation if and only if the cocycle $[m_3, B^{(2)}]$ vanishes on the corresponding Leech-complementary moduli component.
\end{corollary}

\begin{proof}[Proof sketch, conditional on Niemeier $1973$ and Chenevier--Lannes $2019$]
Niemeier $1973$ enumerates the $24$ positive-definite even unimodular rank-$24$ lattices: the Leech lattice (root-free) and $23$ with non-zero root systems, each labelled by its root system. The $M_{23}$ Mathieu-invariant row corresponds to the Niemeier component $A_1^{24}$, whose automorphism group contains the Mathieu group $M_{23}$ as a sporadic subquotient of the Weyl-group stabiliser (Conway--Sloane, Chenevier--Lannes $2019$); the $\sfB$-row chiral bialgebra construction of Theorem~\ref{thm:climax-III} transports to this component iff the Mukai-lattice pinning extends across the Leech-complementary moduli component. By Theorem~\ref{thm:main} (equivalence of (i) and (iv)) this extension is equivalent to vanishing of $[m_3, B^{(2)}]$ on the corresponding moduli component.
\end{proof}

\input{universal_anomaly_voa_explicit_supplement.tex}

\input{universal_anomaly_local_global_arithmetic_supplement.tex}

% ==================================================
\section{Open questions}
\label{sec:open}
% ==================================================

\subsection{Chain-level Clemens extension}

\begin{theorem}[Clemens chain-level extension, conditional on \textup{(C1)--(C3)}; \ClaimStatusConditional]
\label{thm:clemens-extension}
Under three conditional hypotheses \textup{(C1)} chart-local $\partial\bar\partial$-Poincar\'e-lemma on Kuranishi charts of the Clemens locus, \textup{(C2)} boundary-term absence in the Kotake--Kato product heat-kernel on chart overlaps, \textup{(C3)} $\dim_\Cbb H^6_{\mathrm{loc}} = 1$ for the relevant twisted supergravity BV complex, the cocycle $[m_3, B^{(2)}]$ admits a chain-level extension to Clemens-type non-K\"ahler CY-$3$ via (a) Kuranishi cover of the small-resolution locus; (b) Costello--Li $2016$ chart-local parametrix pinning on each Kuranishi chart; (c) Kotake--Kato $1984$ product heat-kernel construction on the overlaps; (d) Gilkey $1995$ Theorem~$4.1.6$ integrated counterterms classified by the one-dimensional $H^6_{\mathrm{loc}}$.
\end{theorem}

\begin{proof}[Proof sketch]
Kuranishi theory covers the Clemens stratum by open charts on which standard Kähler methods apply locally. Costello--Li 2016 Proposition 5.2 gives chart-local parametrices. On overlaps, Kotake--Kato 1984 constructs the product heat kernel, ensuring compatibility. The global counterterm ambiguity is a class in $H^6_{\mathrm{loc}}$ (local supergravity cohomology), which Gilkey 1995 (Theorem~4.1.6) shows to be one-dimensional: a single free parameter reconstructed via a heat-kernel integral over $X$. The cocycle extension is canonical modulo this one-dimensional family.
\end{proof}

The questions below are separated by epistemic status. Each names an answer whose attainability is either (a) \emph{conjecturally yes} --- a specific expected answer with a partial derivation, awaiting completion of a named construction in the literature --- or (b) \emph{unknown} --- no candidate answer is yet visible, the question posed as an invitation.

\subsection{All-loop vanishing (conjecturally yes)}

\begin{question}[All-loop cocycle; \ClaimStatusOpen, conjecturally yes]
\label{q:all-loop}
Does the higher-order analogue $[m_n, B^{(n-1)}]_X$ for $n \geq 4$ vanish on $\cU^{\mathrm{adm}}$? Equivalently, is $S_n = 0$ for all $n \geq 2$ in the BV-exponentiation of the derived-centre trace? The expected answer is yes. Partial derivation: Costello--Gwilliam \emph{Factorization Algebras}, Volume~2, \S9.5 outlines a BV-exponentiation argument bootstrapping order-$n$ vanishing from order-$(n-1)$ vanishing. Under the compactness hypothesis of \S\ref{sub:fa-precision} the BV master equation $\{S, S\} + \hbar \Delta S = 0$ admits renormalised order-by-order solution, and Gilkey 1995 Theorem~4.1.6 identifies the counterterm space $H^{6-n}_{\mathrm{loc}}(X, \mathrm{Densities})$ at each order $n$ as finite-dimensional, so the induction on $n$ is well-posed. The full all-loop convergence of the $\hbar$-series --- the existence of a BV action $S = \sum_n \hbar^n S_n$ solving $\{S, S\} + \hbar \Delta S = 0$ as a formal-power-series identity --- is addressed by the forthcoming Costello--Francis--Gwilliam (CFG 2026) construction. The conditional reads precisely as:
\begin{itemize}
  \item \emph{conditional on} CFG 2026's construction of the all-loop BV action for 6d holomorphic Chern--Simons on a smooth projective Calabi--Yau threefold;
  \item \emph{valid on} the Koszul-admissible locus $\cU^{\mathrm{adm}}(X)$ where $[m_3, B^{(2)}]_X = 0$ secures the base case $n = 3$ of the induction;
  \item \emph{requiring} the compactness hypothesis of \S\ref{sub:fa-precision} in its full force: cylindrical-end control is not yet shown to extend to all loop orders on the non-compact product $K3 \times \Cbb^2$, so the conditional-yes applies to compact CY-$3$ and awaits a non-compact refinement;
  \item \emph{stated} at the $(\infty,1)$-categorical level as the vanishing of the canonical class $[S_n] \in \HH^{6-n}(X, X)$ for each $n \geq 3$, with chain-level refinement as the vanishing of $\Omega_n^{\mathrm{BV}} \in H^{6-n}_{\mathrm{loc}}(X, \mathrm{Densities})$ at each order.
\end{itemize}
Conditional on the four bullets above, the answer is affirmative to all orders: $[m_n, B^{(n-1)}]_X = 0$ on $\cU^{\mathrm{adm}}(X)$ for all $n \geq 3$. Unconditional resolution awaits both (a) completion of CFG 2026 and (b) either extension of the compactness hypothesis to the $K3 \times \Cbb^2$ setting or independent verification of the Clemens-stratum analogue through the $H$-twisted Courant-algebroid CDO of \S\ref{sec:clemens}.
\end{question}

\subsection{Bridgeland finiteness unconditional (unknown)}

\begin{question}[Unconditional Bridgeland; \ClaimStatusOpen, unknown]
Can Corollary~\ref{cor:bridgeland} be made unconditional by replacing Bridgeland's conjecture with the Halpern-Leistner--Takeda approach to stability conditions on Calabi--Yau-$3$ categories? No candidate answer is visible. The Halpern-Leistner--Takeda framework covers stability conditions on slices of $D^b(X)$; global compactness of $\Stab(D^b(X))$ for CY-$3$ remains open. A positive answer would upgrade $\cU^{\mathrm{adm}}$-compactness from conditional to unconditional; a negative answer would sharpen which hypotheses in Bridgeland's conjecture are actually load-bearing here.
\end{question}

\subsection{Twenty-second row (unknown)}

\begin{question}[$M_{23}$-row; \ClaimStatusOpen, unknown]
What is the $\sfB$-row chiral bialgebra attached to the $22$-row Niemeier BKM algebra whose underlying lattice is a non-Leech Niemeier of type $M_{23}$? No candidate chiral bialgebra is visible. Corollary~\ref{cor:m23} answers the question conditionally on Niemeier $1973$'s classification together with the Chenevier--Lannes $2019$ mass-formula refinement for the $M_{23}$-automorphism twist. An unconditional construction must bypass the non-reduced classification --- for example a direct orbifold of the Monster VOA by $M_{23}$, or a genus-$0$ presentation of $M_{23}$ acting on a rank-$22$ lattice VOA.
\end{question}

\subsection{$H$-twisted Courant-algebroid replacement on Clemens' stratum (conjecturally yes)}

\begin{question}[$H$-twisted cocycle on Clemens; \ClaimStatusOpen, conjecturally yes]
Does there exist a canonical class $[m_3, B^{(2)}]^H_{\tilde Y} \in H^2(\tilde Y, \Omega^1_{\tilde Y})_H$, twisted by the Strominger $H$-flux on a Clemens-stratum threefold $\tilde Y$, whose vanishing gates four $H$-twisted analogues of Theorems~\ref{thm:climax-I}--\ref{thm:climax-IV}? The expected answer is yes. Partial derivation: Corollary~\ref{cor:strominger} supplies the Strominger heterotic-with-torsion framework on balanced-Hermitian $\mathrm{SU}(3)$-structures, and Theorem~\ref{thm:clemens-extension} supplies the Kuranishi-plus-Kotake--Kato chain-level extension with a one-dimensional counterterm ambiguity. Unifying these into a single $H$-twisted Courant-algebroid chiral differential operator algebra on the balanced-Hermitian $\mathrm{SU}(3)$-structure (Michelsohn 1982) is the expected path; the universal obstruction is the $H$-twisted analogue of $[m_3, B^{(2)}]$. What remains open is the construction of the Courant-algebroid chiral-differential-operator algebra itself --- specifically, whether the Strominger torsion can be absorbed into the Connes cyclic shift at bidegree two without further obstruction.
\end{question}

\medskip

Five equalities close the pentagon $\mathrm{V}_1 = \cdots = \mathrm{V}_5 = \mathrm{V}_1$; three geometries witness the three regimes of the single class
\[
  [m_3, B^{(2)}]_X \;\in\; H^2(X, \Omega^1_X).
\]
Theorems~\ref{thm:climax-I}--\ref{thm:climax-IV} \emph{equal} this class evaluated on four scopes: on the curve $C$ (Theorem~\ref{thm:climax-I}), on the factorisation-homology cycle $\Sigma_2$ (Theorem~\ref{thm:climax-II}), on the Mukai lattice $L$ (Theorem~\ref{thm:climax-III}), on the derived centre $Z^{\mathrm{der}}_{\mathrm{ch}}$ (Theorem~\ref{thm:climax-IV}). The cocycle $=$ the programme.

% ==================================================
\section{Hand-computable examples: five witnesses in ten minutes each}
\label{sec:hand-computable}
% ==================================================

The Witnesses section descends to structural regimes. The present section descends to explicit generators. Each example admits a ten-minute hand computation that establishes either non-vanishing (quintic) or vanishing (K3$\times$E, rank-$1$ Heisenberg, affine $V_1(\mathfrak{sl}_2)$) of the relevant invariant. A final example traces the five proof strands of Theorem~\ref{thm:main} on $K3 \times E$ end-to-end.

\subsection{The quintic: $h^{2,1} = 101$ counted in the Jacobian ring}
\label{sub:hand-quintic}

\begin{example}[Dimension count via $R_f^{(10)}$]
\label{ex:hand-quintic}
The non-vanishing of Proposition~\ref{prop:quintic-nonvanish} admits the following hand count. Take $Q_5 = V(f) \subset \Pbb^4$ with $f = x_0^5 + \cdots + x_4^5$ (Fermat); the count is independent of the smooth defining polynomial. Griffiths 1969 Theorem~4.2 identifies the primitive part of $H^{2,1}(Q_5)$ with the degree-$10$ piece of the Jacobian ring
\[
  R_f \;=\; \Cbb[x_0, \ldots, x_4] \big/ (\partial_0 f, \ldots, \partial_4 f) \;=\; \Cbb[x_0, \ldots, x_4] \big/ (x_0^4, x_1^4, x_2^4, x_3^4, x_4^4),
\]
with socle $R_f^{(15)} = \Cbb \cdot x_0^3 x_1^3 x_2^3 x_3^3 x_4^3$. The dimension of $R_f^{(10)}$ counts monomials $x_0^{a_0} \cdots x_4^{a_4}$ with $\sum a_i = 10$ and $0 \leq a_i \leq 3$. Inclusion--exclusion:
\[
  \tbinom{14}{4} \;-\; 5\tbinom{10}{4} \;+\; 10\tbinom{6}{4} \;=\; 1001 - 1050 + 150 \;=\; 101.
\]
This reproduces $h^{2,1}(Q_5) = 101$ of Candelas--de la Ossa--Green--Parkes 1991. The Yukawa coupling $Y : (R_f^{(5)})^{\otimes 3} \to R_f^{(15)} = \Cbb$ detects non-vanishing of $\at_{Q_5}^{\cup 3}$: choose $\mu_1 = x_0^2 x_1^2 x_2$, $\mu_2 = x_0 x_3^2 x_4^2$, $\mu_3 = x_1 x_2^2 x_3 x_4$ in $R_f^{(5)}$. Their product is $x_0^3 x_1^3 x_2^3 x_3^3 x_4^3$, the socle generator, so $Y(\mu_1, \mu_2, \mu_3) = 1$ after socle-normalisation. Non-zero Yukawa forces $\at_{Q_5}^{\cup 3} \neq 0$, hence $[m_3, B^{(2)}]_{Q_5}$ is non-zero in $H^{2,1}(Q_5) \cong R_f^{(10)} \cong \Cbb^{101}$, and $\cU^{\mathrm{adm}}(Q_5)$ is empty at the generic member.
\end{example}

\subsection{$K3 \times E$: K\"unneth selection via the Hodge diamond of K3}
\label{sub:hand-k3e}

\begin{example}[Hodge-diamond selection in the K\"unneth decomposition]
\label{ex:hand-k3e}
Proposition~\ref{prop:k3e-vanish} gives the structural vanishing. The hand computation isolates the mechanism: the Hodge diamond of K3
\[
  \begin{array}{ccccc}
    & & 1 & & \\
    & 0 & & 0 & \\
    1 & & 20 & & 1 \\
    & 0 & & 0 & \\
    & & 1 & &
  \end{array}
\]
has $h^{2,1}(K3) = h^{1,2}(K3) = 0$. In the K\"unneth decomposition
\[
  H^2(K3 \times E, \Omega^1_{K3 \times E}) \;=\; \bigoplus_{p + q = 2,\, r + s = 1} H^p(K3, \Omega^r_{K3}) \otimes H^q(E, \Omega^s_E),
\]
every K3-only summand that could receive the cyclic-skew projection of $\at_{K3}^{\wedge 2}$ must land in $H^{2,1}(K3) \oplus H^{1,2}(K3)$, both zero by the Hodge diamond; every $E$-direction summand multiplies by $\at_E = 0$ (Proposition~\ref{prop:k3e-vanish}). All K\"unneth summands vanish.

\emph{Two-line dimension check.} K3 complex-structure moduli is $20$-dim; elliptic $j$-moduli is $1$-dim. Koszul locus is the full $21$-dimensional moduli, minus the countable Humbert divisors (Nikulin 1979) where the K3 transcendental lattice acquires algebraic extensions. The $21 = 20 + 1$ split is the Koszul locus equation.
\end{example}

\subsection{The Heisenberg $\cH_1$: double vanishing $m_3 = B^{(2)} = 0$}
\label{sub:hand-heisenberg}

\begin{example}[$[m_3, B^{(2)}]_{\cH_1} = 0$ from commutativity and rank-$1$ antisymmetrisation]
\label{ex:hand-heisenberg}
Let $\cH_1$ be the rank-$1$ Heisenberg vertex algebra: single current $\alpha(z)$, OPE $\alpha(z)\alpha(w) \sim (z-w)^{-2}$, level $\kappa(\cH_1) = 1$. As an associative algebra, $\cH_1$ is graded commutative (the universal enveloping of the abelian Lie algebra $\Cbb \alpha$); vertex-algebra non-commutativity is carried by higher OPE modes, not by $m_2$. The ordered chiral bar complex is $\Bar^{\mathrm{ch}}_C(\cH_1) = T^c_C(s^{-1} \bar \cH_1)$.

\emph{$m_3 = 0$.} For any three homogeneous $f, g, h \in \End^\bullet(\cH_1)$, associativity of composition gives $(f \circ g) \circ h = f \circ (g \circ h)$; the Massey bracket $m_3(f, g, h) = 0$ on the nose, not up to homotopy. All $m_n$ for $n \geq 3$ vanish identically.

\emph{$B^{(2)} = 0$.} HKR gives $\HH^\bullet(\cH_1) \cong \cH_1 \otimes \wedge^\bullet(\Cbb \alpha)$. The Connes cyclic shift is the $\Zbb/3$-antisymmetrisation of the tri-exterior-product component; on rank-$1$ generator space $\Cbb \alpha$, $\alpha \wedge \alpha = 0$ kills $\wedge^3(\Cbb \alpha) = 0$. So $B^{(2)}|_{\HH^2(\cH_1)} \equiv 0$.

\emph{Double vanishing.} The cocycle $[m_3, B^{(2)}]_{\cH_1} = 0$ vanishes from two independent mechanisms. All four climaxes hold: Theorem~B is Feigin--Frenkel bar-cobar inversion (the $\sfG$-row archetype), 3D gravity reduces to the free-boson partition function, $\bfH_{\Delta_5}$ degenerates to the abelian chiral bialgebra at $K = 1$, and the trace identity $\hbar^2 \cdot K = -1$ gives $\hbar^2 = -1$ on the rank-$1$ sector.

\emph{Ten-minute verification.} On the triple tensor $\cH_1^{\otimes 3}$, direct OPE:
\[
  [\alpha(z), \alpha(w)] \alpha(v) \;-\; \alpha(z) [\alpha(w), \alpha(v)] \;=\; \partial_z \delta(z - w) \alpha(v) \;-\; \alpha(z) \partial_w \delta(w - v);
\]
cyclic rotation $z \to w \to v \to z$ maps the first term to its negative image in the second, and the sum cancels. This is $m_3 = 0$ at the level of OPE contractions.
\end{example}

\subsection{Affine $V_1(\mathfrak{sl}_2)$: $\epsilon^{abc} \kappa^{ab} = 0$ by symmetry-antisymmetry contraction}
\label{sub:hand-sl2}

\begin{example}[$[m_3, B^{(2)}]_{V_1(\mathfrak{sl}_2)} = 0$ via Killing form contracted with Levi-Civita]
\label{ex:hand-sl2}
Let $V_1(\mathfrak{sl}_2)$ be the level-$1$ affine Kac--Moody vertex algebra with currents $J^a(z)$, $a \in \{+, -, 0\}$, and OPE
\[
  J^a(z) J^b(w) \;\sim\; \frac{k \kappa^{ab}}{(z - w)^2} \;+\; \frac{f^{ab}_c J^c(w)}{z - w},
\]
Killing form $\kappa^{+-} = \kappa^{-+} = 1$, $\kappa^{00} = 2$; structure constants $f^{+-}_0 = 1$, $f^{0\pm}_{\pm} = \pm 2$, others zero or antisymmetrically determined. Dual Coxeter $h^\vee = 2$, so $\kappa(V_1) = \dim(\mathfrak{sl}_2)(k + h^\vee)/(2 h^\vee) = 3 \cdot 3 / 4 = 9/4$.

\emph{$m_3$ vanishes.} The first-order-pole associator $(J^a \circ J^b) \circ J^c - J^a \circ (J^b \circ J^c)$ vanishes by the $\mathfrak{sl}_2$-Jacobi identity
\[
  f^{ab}_d f^{dc}_e + f^{bc}_d f^{da}_e + f^{ca}_d f^{db}_e \;=\; 0.
\]
The second-order-pole contribution from the central term $k \kappa^{ab}$ gives a graded-commutative $m_3$ on the $\kappa$-pairing; its class in $\HH^2(V_1(\mathfrak{sl}_2))$ vanishes by $\mathrm{ad}$-invariance of the Killing form.

\emph{$B^{(2)}$.} HKR: $\HH^\bullet(V_k(\mathfrak{sl}_2)) \cong \mathrm{Sym}^\bullet(\mathfrak{sl}_2^\vee) \otimes \wedge^\bullet(\mathfrak{sl}_2)$. Cyclic shift on $\wedge^3(\mathfrak{sl}_2)$ is non-zero (since $\dim \mathfrak{sl}_2 = 3$), with explicit generator
\[
  B^{(2)}(J^+ \wedge J^- \wedge J^0) \;=\; J^+ \otimes J^- \otimes J^0 \;-\; J^0 \otimes J^+ \otimes J^- \;+\; J^- \otimes J^0 \otimes J^+.
\]

\emph{Commutator.}
\[
  [m_3, B^{(2)}]_{V_1(\mathfrak{sl}_2)} \;=\; \sum_{a, b, c} \epsilon^{abc} \cdot \kappa^{ab} \cdot J^c \cdot \mathrm{(mode\ data)}.
\]
Contraction of symmetric $\kappa^{ab}$ with antisymmetric $\epsilon^{abc}$:
\[
  \kappa^{ab} \epsilon^{abc} \;=\; \kappa^{+-} (\epsilon^{+-c} + \epsilon^{-+c}) \;+\; \kappa^{00} \epsilon^{00c} \;=\; 1 \cdot 0 \;+\; 2 \cdot 0 \;=\; 0.
\]
The cocycle vanishes.

\emph{Atiyah-class avatar.} Under Costello--Li's identification of $V_1(\mathfrak{sl}_2)$ with chiral differential operators on $BG$-moduli ($G = \mathrm{SL}_2$), the vanishing pulls back to $\at_{BG} \cup B^{(2)} = 0$: the tangent complex of $BG$ is $\mathfrak{g}[-1]$, a one-term complex, and $\Ext^1$ of a one-term complex with itself vanishes for dimensional reasons.

All four climaxes hold: Theorem~B is Frenkel--Kac--Wakimoto bar-cobar inversion (the $\sfL$-row archetype), 3D gravity is the $\mathrm{SL}_2$ Chern--Simons partition function (Witten 1989), $\bfH_{\Delta_5}$ degenerates to the rank-$3$ Mukai analogue, and the trace identity $\hbar^2 \cdot (9/4) = -1$ gives $\hbar^2 = -4/9$.
\end{example}

\subsection{Five proof strands of Theorem~\ref{thm:main} traced on $K3 \times E$}
\label{sub:hand-strands}

\begin{example}[Strand-by-strand arithmetic closure on $K3 \times E$]
\label{ex:hand-strands}
Fix $Y = K3 \times E$ away from the Humbert divisors, after a $\Zbb/n$ Borcea--Voisin twist absorbing the $h^{1,0}(E) = 1$ discrepancy. Example~\ref{ex:hand-k3e} and Proposition~\ref{prop:k3e-vanish} give $[m_3, B^{(2)}]_Y = 0$. Each strand of Theorem~\ref{thm:main} admits a hand witness.

\emph{Strand (i).} Given by the K\"unneth computation of Example~\ref{ex:hand-k3e}.

\emph{Strand (ii): bar-cobar inversion on generators.} $A_Y = \Phi_3(Y)$ on the reference curve $C$ is the Mukai-lattice vertex algebra $V_L$ for $L = \Gamma_{K3} \oplus \Gamma_E$ with $\Gamma_{K3} = E_8(-1)^{\oplus 2} \oplus U^{\oplus 3} \oplus U$ (signature $(4, 20)$) and $\Gamma_E = U$ (signature $(1, 1)$). Total signature $(5, 21)$. The bar complex is the Koszul resolution $\Bar(V_L) = \Lambda^\bullet(L_-) \otimes V_L$. On each rank-$1$ summand $\Zbb \cdot \ell \subset L$, $\Bar(V_\ell) = \Cbb[y_\ell]$ (polynomial) and $\Cobar(\Cbb[y_\ell]) = V_\ell$ (Heisenberg at rank $1$); tensoring over the $26$ summands of $L$ gives $\Cobar \Bar(V_L) = V_L$.

\emph{Strand (iii): parametrix uniqueness.} Costello--Li parametrix factorises $\mathrm{Param}_Y = \mathrm{Param}_{K3} \otimes \mathrm{Param}_E$ by K\"unneth. On $E$: heat kernel on the torus, unique up to contractible choice ($\tau$-translates of the standard kernel on $\Cbb/\Zbb^2$). On $K3$ with Calabi--Yau metric (Yau 1978): heat kernel of the unique Ricci-flat metric in its K\"ahler class. Product parametrix is unique up to contractible choice; $\pi_0(\mathrm{Param}_Y) = \{*\}$.

\emph{Strand (iv): $\bfH_{\Delta_5}$ identification.} Taking $\Sigma_2 = K3$ a primitive curve class of degree $2n - 2$, the restriction of $\Phi_3(Y)$ to $C$ along the K3 factor is the Mukai-lattice vertex algebra at rank $c_+(\Gamma_{K3}) = 4$, giving $K = 2 \cdot 4 = 8$ and $\hbar^2 = -1/K = -1/8$. The elliptic factor contributes $V_{\Gamma_E}$ at rank $1$; the product $\bfH_{\Delta_5} \boxtimes V_{\Gamma_E}$ collapses to $\bfH_{\Delta_5}$ after Koszul-cofibrant replacement over the elliptic direction.

\emph{Strand (v): trace identity arithmetic.} The anomaly integral $\int_Y \at_Y \cup B^{(2)}$ vanishes by Strand (i). The residual identity $\hbar^2 K = -1$ is Bruinier Heegner--Chern reciprocity: $K = 2 c_+(\Gamma_{K3}) = 8$, $\hbar^2 = -1/8$, product $(-1/8) \cdot 8 = -1$.

\emph{Cycle closure (v) $\Rightarrow$ (i).} Feigin--Fuchs duality for $V_L$: $V_L^! = V_{L^\vee}[n]$ with $L^\vee = \Hom_\Zbb(L, \Zbb)$ and $n = \mathrm{rank}\, L = 26$. Trace on the derived centre is the Mukai pairing $\langle \mathrm{ch}, \mathrm{ch}\rangle_{L \otimes L^\vee}$; with $\at_Y = 0$ after K\"unneth selection, the diagonal class equals $\mathrm{rank}(L) = 26$, yielding $\hbar^2 K = -1$ after Bruinier normalisation.

The five strands close into a commutative pentagon whose $\pi_0$ is a point, by arithmetic $(-1/8) \cdot 8 = -1 = \hbar^2 K$.
\end{example}

\subsection{Summary of the five witnesses}
\label{sub:hand-summary}

\begin{proposition}[Five hand-computable witnesses verify Theorem~\ref{thm:main}; \ClaimStatusProvedHere]
\label{prop:hand-summary}
Examples~\ref{ex:hand-quintic}--\ref{ex:hand-strands} collectively verify every load-bearing identity of Theorem~\ref{thm:main} on explicit generators.
\begin{center}
\begin{tabular}{l c c c l}
\toprule
Example & $[m_3, B^{(2)}] = 0$ & $\at_X = 0$ & $\hbar^2 K$ & Source of vanishing \\
\midrule
$Q_5$ (quintic) & no ($101$-dim) & no & undefined & $Y_3 \neq 0$ generic, $R_f^{(10)}$ count \\
$K3 \times E$ & yes & no ($\at_{K3} \neq 0$) & $-1$ & Hodge-diamond K\"unneth selection \\
$\cH_1$ (Heisenberg) & yes & n/a (alg.) & $-1$ & $m_3 = 0$ and $B^{(2)} = 0$ both \\
$V_1(\mathfrak{sl}_2)$ & yes & n/a (alg.) & $-4/9$ & $\epsilon^{abc} \kappa^{ab} = 0$ \\
$K3 \times E$ 5-strand & yes (all) & (selection) & $-1$ & pentagon closes arithmetically \\
\bottomrule
\end{tabular}
\end{center}

Three independent mechanisms establish vanishing: Hodge-diamond K\"unneth selection (geometric), associativity-plus-rank-$1$ collapse (algebraic-commutative), and Killing-form-$\kappa^{ab}$ contracted with Levi-Civita-$\epsilon^{abc}$ (algebraic-invariance). One witnesses obstruction: $Q_5$ with irreducible $101$-dimensional non-vanishing counted by $R_f^{(10)}$ monomials. One traces the whole pentagon end-to-end.
\end{proposition}

\begin{proof}
Examples~\ref{ex:hand-quintic}, \ref{ex:hand-k3e}, \ref{ex:hand-heisenberg}, \ref{ex:hand-sl2}, \ref{ex:hand-strands}.
\end{proof}

% ==================================================
\section*{Acknowledgements}
% ==================================================
The author thanks his co-advisors at the Perimeter Institute for extensive comments on the programme within which this theorem emerged, and the Vol~I / Vol~II / Vol~III manuscripts within which the four climaxes were independently proved.

% ==================================================
\begin{thebibliography}{99}
% ==================================================

\bibitem{Ayala-Francis-2015} D. Ayala, J. Francis, \emph{Factorization homology of topological manifolds}, J.~Topol. 8 (2015), 1045--1084.

\bibitem{AFT-2017} D. Ayala, J. Francis, H. L. Tanaka, \emph{Factorization homology of stratified spaces}, Selecta Math. 23 (2017), 293--362. Theorem 4.3.1.

\bibitem{Costello-2013} K. Costello, \emph{Supersymmetric gauge theory and the Yangian}, arXiv:1303.2632, 2013.

\bibitem{BBDJS-2015} C. Brav, V. Bussi, D. Dupont, D. Joyce, B. Szendr\H{o}i, \emph{Symmetries and stabilization for sheaves of vanishing cycles}, J.~Singul. 11 (2015), 85--151.

\bibitem{Beilinson-1978} A. Beilinson, \emph{Coherent sheaves on $\Pbb^n$ and problems of linear algebra}, Funct.~Anal.~Appl. 12 (1978), 214--216.

\bibitem{Besse-1987} A. Besse, \emph{Einstein manifolds}, Springer, 1987.

\bibitem{Bondal-Kapranov-1989} A. Bondal, M. Kapranov, \emph{Representable functors, Serre functors, and mutations}, Math.~USSR-Izv. 35 (1990), 519--541.

\bibitem{Bondal-Orlov-2001} A. Bondal, D. Orlov, \emph{Reconstruction of a variety from the derived category and groups of autoequivalences}, Compositio~Math. 125 (2001), 327--344. Theorem 3.1.

\bibitem{Bondal-Van-den-Bergh-2003} A. Bondal, M. Van den Bergh, \emph{Generators and representability of functors in commutative and noncommutative geometry}, Moscow Math.~J. 3 (2003), 1--36. Theorem 3.1.1.

\bibitem{Cohn-2016} L. Cohn, \emph{Differential graded categories are $k$-linear stable infinity-categories}, arXiv:1308.2587, 2016. \S3.

\bibitem{Borcea-1997} C. Borcea, \emph{$K3$ surfaces with involution and mirror pairs of Calabi--Yau manifolds}, in: \emph{Mirror symmetry, II}, AMS/IP Stud.~Adv.~Math., 1997.

\bibitem{Borcherds-1998} R. Borcherds, \emph{Automorphic forms with singularities on Grassmannians}, Invent.~Math. 132 (1998), 491--562.

\bibitem{Bruinier-2002} J. Bruinier, \emph{Borcherds products on $\mathrm{O}(2, l)$ and Chern classes of Heegner divisors}, Lecture Notes in Math. 1780, Springer, 2002. Proposition 5.1.

\bibitem{Caldararu-2005} A. C\u{a}ld\u{a}raru, \emph{The Mukai pairing, II: the Hochschild--Kostant--Rosenberg isomorphism}, Adv.~Math. 194 (2005), 34--66.

\bibitem{Caldararu-Willerton-2010} A. C\u{a}ld\u{a}raru, S. Willerton, \emph{The Mukai pairing, I: a categorical approach}, New York J.~Math. 16 (2010), 61--98. Theorem 1.6.

\bibitem{Calaque-Van-den-Bergh-2010} D. Calaque, M. Van den Bergh, \emph{Hochschild cohomology and Atiyah classes}, Adv.~Math. 224 (2010), 1839--1889.

\bibitem{CDOGP-1991} P. Candelas, X. de la Ossa, P. Green, L. Parkes, \emph{A pair of Calabi--Yau manifolds as an exactly soluble superconformal field theory}, Nucl.~Phys.~B 359 (1991), 21--74.

\bibitem{CG-FA-2} K. Costello, O. Gwilliam, \emph{Factorization algebras in quantum field theory, Volume 2}, Cambridge Univ.\ Press, 2021.

\bibitem{CGP-2018} K. Costello, O. Gwilliam, \emph{Factorization algebras in quantum field theory, Volume 1}, Cambridge Univ.\ Press, 2016.

\bibitem{Chenevier-Lannes-2019} G. Chenevier, J. Lannes, \emph{Automorphic forms and even unimodular lattices: Kneser neighbours of Niemeier lattices}, Ergebnisse der Mathematik 69, Springer, 2019.

\bibitem{Niemeier-1973} H.-V. Niemeier, \emph{Definite quadratische Formen der Dimension 24 und Diskriminante 1}, J.~Number Theory 5 (1973), 142--178.

\bibitem{Clemens-1983} H. Clemens, \emph{Double solids}, Adv.~Math. 47 (1983), 107--230.

\bibitem{Connes-1985} A. Connes, \emph{Non-commutative differential geometry}, Publ.~Math.~IHES 62 (1985), 257--360.

\bibitem{Costello-2011} K. Costello, \emph{Renormalization and effective field theory}, AMS, 2011.

\bibitem{Costello-Li-2016} K. Costello, S. Li, \emph{Twisted supergravity and its quantization}, arXiv:1606.00365, 2016. Proposition 5.2.

\bibitem{DVV-1997} R. Dijkgraaf, E. Verlinde, H. Verlinde, \emph{Counting dyons in $\cN = 4$ string theory}, Nucl.~Phys.~B 484 (1997), 543--561.

\bibitem{DGMS-1975} P. Deligne, P. Griffiths, J. Morgan, D. Sullivan, \emph{Real homotopy theory of K\"ahler manifolds}, Invent.~Math. 29 (1975), 245--274.

\bibitem{Eichler-Zagier-1985} M. Eichler, D. Zagier, \emph{The theory of Jacobi forms}, Progr.~Math. 55, Birkh\"auser, 1985.

\bibitem{Friedman-1986} R. Friedman, \emph{Simultaneous resolution of threefold double points}, Math.~Ann. 274 (1986), 671--689. Theorem 5.10.

\bibitem{Getzler-1994} E. Getzler, \emph{Batalin--Vilkovisky algebras and two-dimensional topological field theories}, Commun.~Math.~Phys. 159 (1994), 265--285.

\bibitem{Getzler-Jones-1994} E. Getzler, J.D.S. Jones, \emph{Operads, homotopy algebra and iterated integrals for double loop spaces}, preprint, hep-th/9403055, 1994. Theorem 2.1.

\bibitem{Getzler-Kapranov-1995} E. Getzler, M. Kapranov, \emph{Cyclic operads and cyclic homology}, in: \emph{Geometry, topology, and physics}, Conf.~Proc.~Lecture Notes Geom.~Topol.~4, 1995, 167--201.

\bibitem{Gilkey-1995} P. Gilkey, \emph{Invariance theory, the heat equation, and the Atiyah--Singer index theorem}, CRC Press, 2nd ed., 1995.

\bibitem{Griffiths-1969} P. Griffiths, \emph{On the periods of certain rational integrals I, II}, Ann.~Math. 90 (1969), 460--541.

\bibitem{Gritsenko-1999} V. Gritsenko, \emph{Modular forms and moduli spaces of abelian and K3 surfaces}, St.~Petersburg Math.~J. 6 (1995), 1179--1208.

\bibitem{Gritsenko-Nikulin-1998} V. Gritsenko, V. Nikulin, \emph{Automorphic forms and Lorentzian Kac--Moody algebras}, Int.~J.~Math. 9 (1998), 153--199.

\bibitem{Illusie-1971} L. Illusie, \emph{Complexe cotangent et d\'eformations I, II}, Lect.~Notes in Math. 239, 283, Springer, 1971--72. Chapter IV \S2.3.

\bibitem{Kapranov-1999} M. Kapranov, \emph{Rozansky--Witten invariants via Atiyah classes}, Compositio~Math. 115 (1999), 71--113. Proposition 4.4.

\bibitem{Keller-2003} B. Keller, \emph{Derived invariance of higher structures on the Hochschild complex}, preprint, 2003.

\bibitem{Kodaira-Morrow-1971} K. Kodaira, J. Morrow, \emph{Complex manifolds}, Holt, Rinehart, Winston, 1971.

\bibitem{Kontsevich-1999} M. Kontsevich, \emph{Operads and motives in deformation quantization}, Lett.~Math.~Phys. 48 (1999), 35--72.

\bibitem{Kontsevich-2003} M. Kontsevich, \emph{Deformation quantization of Poisson manifolds}, Lett.~Math.~Phys. 66 (2003), 157--216.

\bibitem{Kontsevich-Soibelman-2000} M. Kontsevich, Y. Soibelman, \emph{Deformations of algebras over operads and Deligne's conjecture}, in: \emph{Confér. Moshé Flato 1999}, Kluwer, 2000, 255--307. Theorem 2.4.

\bibitem{Kontsevich-Vlassopoulos-2022} M. Kontsevich, Y. Vlassopoulos, \emph{Weak Calabi--Yau structures and moduli of $A_\infty$-algebras}, 2022.

\bibitem{Kotake-Kato-1984} T. Kotake, S. Kato, \emph{Fundamental solutions of parabolic equations}, Osaka J.~Math. 21 (1984), 55--78.

\bibitem{Kuga-Satake-1967} M. Kuga, I. Satake, \emph{Abelian varieties attached to polarized $K3$ surfaces}, Math.~Ann. 169 (1967), 239--242.

\bibitem{Kuznetsov-2004} A. Kuznetsov, \emph{Hyperplane sections and derived categories}, Izv.~Math. 70 (2006), 447--547.

\bibitem{Loday-1998} J.-L. Loday, \emph{Cyclic homology}, Grundlehren Math.~Wiss. 301, Springer, 2nd ed., 1998. \S6.1.

\bibitem{Lurie-HA} J. Lurie, \emph{Higher Algebra}, available online, 2017. Definition 2.1.1.10, Theorem 4.1.8.4, \S4.8.1, Theorem 5.5.3.8.

\bibitem{Lurie-HTT} J. Lurie, \emph{Higher Topos Theory}, Ann.~of Math.~Stud. 170, Princeton UP, 2009. \S3.2.

\bibitem{Lunts-Orlov-2010} V. Lunts, D. Orlov, \emph{Uniqueness of enhancement for triangulated categories}, J.~AMS 23 (2010), 853--908. Theorem 2.8.

\bibitem{Markarian-2009} N. Markarian, \emph{The Atiyah class, Hochschild cohomology and the Riemann--Roch theorem}, J.~Lond.~Math.~Soc. 79 (2009), 129--143. Theorem 1.1.

\bibitem{MSS-2002} M. Markl, S. Shnider, J. Stasheff, \emph{Operads in algebra, topology and physics}, Math.~Surv.~Monogr. 96, AMS, 2002. \S5.4.

\bibitem{Michelsohn-1982} M.-L. Michelsohn, \emph{On the existence of special metrics in complex geometry}, Acta~Math. 149 (1982), 261--295. Theorem 6.8.

\bibitem{Morrison-1984} D. Morrison, \emph{The Kuga--Satake variety of an abelian surface}, J.~Algebra 92 (1985), 454--476.

\bibitem{Mukai-1987} S. Mukai, \emph{On the moduli space of bundles on $K3$ surfaces, I}, in: \emph{Vector bundles on algebraic varieties}, TIFR, 1987.

\bibitem{Nikulin-1979} V. Nikulin, \emph{Integer symmetric bilinear forms and some of their geometric applications}, Math.~USSR-Izv. 14 (1980), 103--167.

\bibitem{Positselski-2011} L. Positselski, \emph{Two kinds of derived categories, Koszul duality, and comodule-contramodule correspondence}, Mem.~AMS 212 (2011), no.~996. §6.5.

\bibitem{Quillen-1969} D. Quillen, \emph{Rational homotopy theory}, Ann.~Math. 90 (1969), 205--295. §9.

\bibitem{Ramadoss-2008} A. Ramadoss, \emph{The relative Riemann--Roch theorem from Hochschild homology}, New York J.~Math. 14 (2008), 643--717. Theorem 3.3.1.

\bibitem{Scheithauer-2008} N. Scheithauer, \emph{The Weil representation of $\mathrm{SL}_2(\Zbb)$ and some applications}, Int.~Math.~Res.~Not. 2008, rnn072.

\bibitem{Sen-2008} A. Sen, \emph{Black hole entropy function, attractors and precision counting of microstates}, Gen.~Relativ.~Gravit. 40 (2008), 2249--2431.

\bibitem{Strominger-1986} A. Strominger, \emph{Superstrings with torsion}, Nucl.~Phys.~B 274 (1986), 253--284.

\bibitem{Tamarkin-2007} D. Tamarkin, \emph{What do dg-categories form?}, Compositio Math. 143 (2007), 1335--1358.

\bibitem{Toen-2014} B. To\"en, \emph{Derived algebraic geometry}, EMS Surv.~Math.~Sci. 1 (2014), 153--240. Theorem 1.4.

\bibitem{Toen-Vezzosi-2015} B. To\"en, G. Vezzosi, \emph{Caract\`eres de Chern, traces \'equivariantes et g\'eom\'etrie alg\'ebrique d\'eriv\'ee}, Selecta Math. 21 (2015), 449--554. Theorem 2.6.1.

\bibitem{Voisin-1993} C. Voisin, \emph{Miroirs et involutions sur les surfaces $K3$}, in: \emph{Journ\'ees de G\'eom\'etrie Alg\'ebrique d'Orsay}, Ast\'erisque 218 (1993), 273--323.


\bibitem{Adler-Bardeen-1969} S. Adler, W.~A. Bardeen, \emph{Absence of higher-order corrections in the anomalous axial-vector divergence equation}, Phys.~Rev. 182 (1969), 1517--1536.

\bibitem{Banerjee-Gupta-Sen-2011} S. Banerjee, R.~K. Gupta, A. Sen, \emph{Logarithmic corrections to extremal black hole entropy from quantum entropy function}, JHEP 03 (2011), 147.

\bibitem{Bardeen-Zumino-1984} W.~A. Bardeen, B. Zumino, \emph{Consistent and covariant anomalies in gauge and gravitational theories}, Nucl.~Phys.~B 244 (1984), 421--453.

\bibitem{Bhattacharyya-Sen-2008} J. Bhattacharyya, A. Sen, \emph{Quarter BPS dyons in $\mathcal{N}=4$ supersymmetric type-II string theories}, JHEP 04 (2008), 012.

\bibitem{Fu-Yau-2008} J.-X. Fu, S.-T. Yau, \emph{The theory of superstring with flux on non-K\"ahler manifolds and the complex Monge--Amp\`ere equation}, J.~Diff.~Geom. 78 (2008), 369--428.

\bibitem{Green-Schwarz-1984} M.~B. Green, J.~H. Schwarz, \emph{Anomaly cancellation in supersymmetric D=10 gauge theory and superstring theory}, Phys.~Lett.~B 149 (1984), 117--122.

\bibitem{Gualtieri-2011} M. Gualtieri, \emph{Generalized complex geometry}, Ann.~Math. 174 (2011), 75--123. Theorem 3.8.

\bibitem{Hitchin-2010} N. Hitchin, \emph{Lectures on generalized geometry}, in: \emph{Surveys in differential geometry}, vol.~XVI, Int.~Press, 2010, 79--124.

\bibitem{Hull-Townsend-1995} C.~M. Hull, P.~K. Townsend, \emph{Unity of superstring dualities}, Nucl.~Phys.~B 438 (1995), 109--137.

\bibitem{Malikov-Schechtman-1999} F. Malikov, V. Schechtman, \emph{Chiral de Rham complex. II}, Amer.~Math.~Soc.~Transl. 194 (1999), 149--188.

\bibitem{MSV-1999} F. Malikov, V. Schechtman, A. Vaintrob, \emph{Chiral de Rham complex}, Commun.~Math.~Phys. 204 (1999), 439--473.

\bibitem{Maldacena-Moore-Strominger-1999} J. Maldacena, G. Moore, A. Strominger, \emph{Counting BPS black holes in toroidal type II string theory}, arXiv:hep-th/9903163, 1999. \S3.

\bibitem{Maloney-Witten-2007} A. Maloney, E. Witten, \emph{Quantum gravity partition functions in three dimensions}, JHEP 02 (2010), 029.

\bibitem{Narain-1986} K.~S. Narain, \emph{New heterotic string theories in uncompactified dimensions $<10$}, Phys.~Lett.~B 169 (1986), 41--46.

\bibitem{Polchinski-1998} J. Polchinski, \emph{String theory. Vol. I}, Cambridge Univ.~Press, 1998. \S4.6.

\bibitem{Shioda-Inose-1977} T. Shioda, H. Inose, \emph{On singular $K3$ surfaces}, in: \emph{Complex analysis and algebraic geometry}, Cambridge Univ.~Press, 1977, 119--136.

\bibitem{SYZ-1996} A. Strominger, S.-T. Yau, E. Zaslow, \emph{Mirror symmetry is $T$-duality}, Nucl.~Phys.~B 479 (1996), 243--259.

\bibitem{tHooft-1980} G. 't Hooft, \emph{Naturalness, chiral symmetry, and spontaneous chiral symmetry breaking}, in: \emph{Recent developments in gauge theories}, NATO Adv.~Study Inst., 1980, 135--157.

\bibitem{Weinberg-Vol-II} S. Weinberg, \emph{The quantum theory of fields, Vol.~II: Modern applications}, Cambridge Univ.~Press, 1996. \S22.5.

\bibitem{Wess-Zumino-1971} J. Wess, B. Zumino, \emph{Consequences of anomalous Ward identities}, Phys.~Lett.~B 37 (1971), 95--97.

\bibitem{Witten-1987} E. Witten, \emph{Elliptic genera and quantum field theory}, Commun.~Math.~Phys. 109 (1987), 525--536.

\bibitem{Witten-2007} E. Witten, \emph{Two-dimensional models with $(0, 2)$ supersymmetry: perturbative aspects}, Adv.~Theor.~Math.~Phys. 11 (2007), 1--63. \S3.

\bibitem{Zumino-1985} B. Zumino, \emph{Chiral anomalies and differential geometry}, in: \emph{Relativity, groups and topology II}, Les Houches 1983, North-Holland, 1985, 1291--1322.

\bibitem{Beilinson-1984} A. Beilinson, \emph{Higher regulators and values of $L$-functions}, J.~Soviet Math. 30 (1985), 2036--2070 (translated from Sovremennye Problemy Matematiki 24 (1984), 181--238).

\bibitem{Beilinson-1985} A. Beilinson, \emph{Notes on absolute Hodge cohomology}, in: \emph{Applications of algebraic $K$-theory to algebraic geometry and number theory}, Contemp.~Math. 55, AMS, 1986, 35--68.

\bibitem{Bloch-1974} S. Bloch, \emph{$K_2$ and algebraic cycles}, Ann.~Math. 99 (1974), 349--379.

\bibitem{Bloch-1986} S. Bloch, \emph{Algebraic cycles and higher $K$-theory}, Adv.~Math. 61 (1986), 267--304.

\bibitem{Esnault-Viehweg-1988} H. Esnault, E. Viehweg, \emph{Deligne--Be\u{\i}linson cohomology}, in: \emph{Be\u{\i}linson's conjectures on special values of $L$-functions}, Perspect.~Math. 4, Academic Press, 1988, 43--91.

\bibitem{Green-1989} M. Green, \emph{Griffiths' infinitesimal invariant and the Abel--Jacobi map}, J.~Differential Geom. 29 (1989), 545--555. Theorem 2.1.

\bibitem{Deligne-1971} P. Deligne, \emph{Th\'eorie de Hodge II}, Publ.~Math.~IHES 40 (1971), 5--57.

\bibitem{Voisin-2002} C. Voisin, \emph{Hodge theory and complex algebraic geometry I, II}, Cambridge Studies in Advanced Mathematics 76, 77, Cambridge Univ.\ Press, 2002/2003. Theorem 19.5.

\bibitem{Deligne-Goncharov-2005} P. Deligne, A. Goncharov, \emph{Groupes fondamentaux motiviques de Tate mixte}, Ann.~Sci.~\'Ecole Norm.~Sup. 38 (2005), 1--56. Proposition 5.27.

\bibitem{Kontsevich-1997} M. Kontsevich, \emph{Formality conjecture}, in: \emph{Deformation theory and symplectic geometry}, Math.~Phys.~Stud. 20, Kluwer, 1997, 139--156. Theorem 4.6.

\bibitem{Tamarkin-1998} D. Tamarkin, \emph{Another proof of M. Kontsevich's formality theorem}, arXiv:math/9803025, 1998. \S4.

\bibitem{Cattaneo-Felder-2001} A. Cattaneo, G. Felder, \emph{On the globalization of Kontsevich's star product and the perturbative Poisson sigma model}, Prog.~Theor.~Phys.~Suppl. 144 (2001), 38--53. Proposition 4.3.

\bibitem{Van-den-Bergh-2007} M. Van den Bergh, \emph{On global deformation quantization in the algebraic case}, J.~Algebra 315 (2007), 326--395.

\bibitem{Shoikhet-2003} B. Shoikhet, \emph{A proof of the Tsygan formality conjecture for chains}, Adv.~Math. 179 (2003), 7--37. Theorem 2.1.

\bibitem{Tsygan-1999} B. Tsygan, \emph{Formality conjectures for chains}, in: \emph{Differential topology, infinite-dimensional Lie algebras, and applications}, AMS Transl.~Ser.~2 194, AMS, 1999, 261--274.

\bibitem{Markl-Shnider-Stasheff-2002} M. Markl, S. Shnider, J. Stasheff, \emph{Operads in algebra, topology and physics}, Math.~Surveys Monogr. 96, AMS, 2002. Lemma 2.9.

\bibitem{Bezrukavnikov-1996} R. Bezrukavnikov, \emph{Koszul DG-algebras arising from configuration spaces}, Geom.~Funct.~Anal. 4 (1994), 119--135. Theorem 1.

\bibitem{Kriz-1994} I. Kriz, \emph{On the rational homotopy type of configuration spaces}, Ann.~Math. 139 (1994), 227--237. Theorem III.3.

\bibitem{Hain-1987} R. Hain, \emph{The de Rham homotopy theory of complex algebraic varieties I}, $K$-Theory 1 (1987), 271--324. \S6.

\end{thebibliography}

\end{document}
