\chapter{W-algebras: Complete Examples}

\section{Principal W-algebras via Drinfeld-Sokolov}

\subsection{Construction}

Following Arakawa \cite{Ara07}, the principal W-algebra is obtained by quantum Drinfeld-Sokolov reduction:
$$\Walg^k(\mathfrak{g}) = H^*_{\DS}(\widehat{\mathfrak{g}}_k, Q_{\DS})$$

\subsection{Generators and Relations}

For $\mathfrak{g} = \mathfrak{sl}_n$:
\begin{itemize}
\item Generators: $W^{(2)}, W^{(3)}, \ldots, W^{(n)}$ of conformal weights $2, 3, \ldots, n$
\item Relations: Determined by null vectors at critical level
\end{itemize}

\section{$\mathcal{W}_3$ Algebra: Complete Analysis}

\subsection{Structure Constants}

The $\mathcal{W}_3$ algebra has generators $T$ (weight 2) and $W$ (weight 3).

OPEs:
\begin{align}
T(z)T(w) &= \frac{c/2}{(z-w)^4} + \frac{2T(w)}{(z-w)^2} + \frac{\partial T(w)}{z-w} \\
T(z)W(w) &= \frac{3W(w)}{(z-w)^2} + \frac{\partial W(w)}{z-w} \\
W(z)W(w) &= \frac{c/3}{(z-w)^6} + \frac{2T(w)}{(z-w)^4} + \frac{\partial T(w)}{(z-w)^3} \\
&+ \frac{1}{(z-w)^2}\left(\frac{3\partial^2 T}{10} + \frac{16}{22+5c}\Lambda(w)\right) + \cdots
\end{align}
where $\Lambda = (TT) - \frac{3}{10}\partial^2 T$.

\subsection{Bar Complex of $\mathcal{W}_3$}

\begin{theorem}[Complete Bar Complex]
At $c = 2$ (critical for $\mathfrak{sl}_3$):

\textbf{Degree 0-3}: Generators
\begin{align}
\bar{B}^0 &= \mathbb{C} \cdot |0\rangle \\
\bar{B}^1 &= 0 \text{ (no weight 1 fields)} \\
\bar{B}^2 &= \mathbb{C} \cdot T \\
\bar{B}^3 &= \mathbb{C} \cdot W
\end{align}

\textbf{Degree 4}: First nontrivial
\begin{align}
\bar{B}^4 &= \mathbb{C}(T \otimes T) \oplus \mathbb{C}\partial^2T \\
d(T \otimes T) &= 2T \\
d(\partial^2T) &= 0
\end{align}

\textbf{Degree 5}:
\begin{align}
\bar{B}^5 &= \mathbb{C}(T \otimes W) \oplus \mathbb{C}(W \otimes T) \oplus \mathbb{C}\partial^2W \\
d(T \otimes W) &= 3W \\
d(W \otimes T) &= 3W \\
d(\partial^2W) &= 0
\end{align}

\textbf{Degree 6}: Complex structure
\begin{align}
\bar{B}^6 = &\mathbb{C}(W \otimes W) \oplus \mathbb{C}(T \otimes T \otimes T) \\
&\oplus \mathbb{C}(T \otimes \partial^2T) \oplus \mathbb{C}\partial^4T
\end{align}
\end{theorem}

\begin{proof}
Use residue calculus with explicit OPEs.

For $d(T \otimes T)$:
$$d(T \otimes T) = \text{Res}_{z_1=z_2}\left[\frac{2T(z_2)dz_1}{(z_1-z_2)^2}\right] = 2T$$

For $d(W \otimes W)$:
$$d(W \otimes W) = \text{Res}_{z_1=z_2}\left[\frac{2T(z_2)dz_1}{(z_1-z_2)^4}\right] = 0$$
(Higher pole gives zero residue for weight reasons.)
\end{proof}

\subsection{Cohomology and Flag Variety}

\begin{theorem}[Geometric Interpretation]
$$H^*(\bar{B}(\mathcal{W}_3)) \cong H^*(\mathfrak{sl}_3/B)$$
the cohomology of the flag variety.
\end{theorem}

Explicitly:
$$H^*(\mathfrak{sl}_3/B) = \mathbb{C}[x_2, x_3]/(x_2^3 - x_3^2)$$
where $x_i$ are Schubert classes.

\section{W-algebras at Critical Level}

\subsection{Feigin-Frenkel Center}

At critical level $k = \critLevel$:

\begin{theorem}[Large Center]
The center of $\Walg^{\critLevel}(\mathfrak{g})$ is:
$$Z(\Walg^{\critLevel}(\mathfrak{g})) \cong \text{Fun}(\text{Op}_{\mathfrak{g}^\vee}(X))$$
functions on the space of $\mathfrak{g}^\vee$-opers.
\end{theorem}

\subsection{Bar Complex at Critical Level}

\begin{theorem}[Dramatic Simplification]
At $k = \critLevel$:
$$\bar{B}(\Walg^{\critLevel}(\mathfrak{g})) = \text{Free}[S_1, \ldots, S_r] \otimes \Omega^*_{\log}$$
where $S_i$ are screening charges.

The differential is:
$$d = \sum_i S_i \otimes d\log(\text{screening})$$
\end{theorem}

\section{Wakimoto Modules and Free Field Realization}

\subsection{Construction}

The Wakimoto module provides a free field realization:
$$\Wakimoto = \text{Free}[\beta_\alpha, \gamma_\alpha, \phi_i]$$
where:
\begin{itemize}
\item $(\beta_\alpha, \gamma_\alpha)$: One pair per positive root
\item $\phi_i$: Cartan generators
\end{itemize}

\subsection{Bar Complex of Wakimoto}

\begin{theorem}[Wakimoto Bar Complex]
$$\bar{B}(\Wakimoto) = \bigotimes_{\alpha \in \Delta_+} \bar{B}(\beta_\alpha\gamma_\alpha) \otimes \bar{B}(\text{Heisenberg}^{\text{rank}(\mathfrak{g})})$$
\end{theorem}

This factorization allows explicit computation.

\subsection{Relation to W-algebras}

\begin{theorem}[DS Reduction]
$$H^*_{Q_{\DS}}(\bar{B}(\Wakimoto)) \cong \bar{B}(\Walg^{\critLevel}(\mathfrak{g}))$$
The BRST cohomology of the Wakimoto bar complex gives the W-algebra bar complex.
\end{theorem}

\section{Koszul Duality for W-algebras}

\subsection{Principal W-algebra Duality}

\begin{theorem}[Langlands Dual W-algebras]
At critical level:
$$\Walg^{\critLevel}(\mathfrak{g})^! = \Walg^{\critLevel}(\mathfrak{g}^\vee)$$
where $\mathfrak{g}^\vee$ is the Langlands dual Lie algebra.
\end{theorem}

\subsection{Non-principal Cases}

For non-principal nilpotent $f$:
$$\Walg^k(\mathfrak{g}, f)^! = \text{Exotic W-algebra}$$
These involve fractional powers and require orbifold techniques.