\chapter{Chiral Hochschild Cohomology and Koszul Duality}

\section{Motivation: The Deformation Problem for Chiral Algebras}

\subsection{Historical Genesis and Physical Motivation}

The development of Hochschild cohomology for chiral algebras emerged from three independent streams of thought that converged in the 1990s. First, physicists studying marginal deformations of conformal field theories needed to understand when a perturbation $S \to S + \lambda \int \phi(z,\bar{z}) d^2z$ preserves conformal invariance. Seiberg \cite{Sei88} recognized that exactly marginal deformations correspond to closed elements in a certain cohomology theory. Second, mathematicians following Gerstenhaber's deformation theory \cite{Ger63} sought to extend Hochschild cohomology to vertex algebras. Third, Beilinson-Drinfeld's formalization of chiral algebras \cite{BD04} as factorization algebras demanded a cohomology theory respecting the geometric structure.

The fundamental question is: Given a chiral algebra $\mathcal{A}$ on a smooth curve $X$, what are its infinitesimal deformations that preserve the chiral structure? In classical algebra, if we deform an associative multiplication $\mu: A \otimes A \to A$ to $\mu_t = \mu + t\phi$, the associativity constraint
\[
\mu_t(\mu_t \otimes \text{id}) = \mu_t(\text{id} \otimes \mu_t)
\]
must hold to first order in $t$. Expanding, we find $\phi$ must satisfy
\[
\mu(\phi \otimes \text{id} - \text{id} \otimes \phi) + \phi(\mu \otimes \text{id} - \text{id} \otimes \mu) = 0
\]
This is precisely the Hochschild 2-cocycle condition. The obstruction to extending to second order lives in $HH^3(A,A)$.

For chiral algebras, the situation is far richer. A deformation must preserve:
\begin{enumerate}
\item The $\mathcal{D}_X$-module structure encoding locality
\item The chiral multiplication $\mu: j_*j^*(\mathcal{A} \boxtimes \mathcal{A}) \to \Delta_*\mathcal{A}$
\item The singularity structure along the diagonal
\item The operator product expansion coefficients
\end{enumerate}

\subsection{Why Configuration Spaces Enter}

The appearance of configuration spaces is not a mathematical convenience but a physical necessity. In quantum field theory, the principle of locality states that operators commute at spacelike separation. On a curve $X$, this means the commutator $[\phi_1(z_1), \phi_2(z_2)]$ must vanish for $z_1 \neq z_2$. All nontrivial structure is thus encoded in the approach $z_1 \to z_2$.

The configuration space $C_n(X) = \{(z_1,\ldots,z_n) \in X^n : z_i \neq z_j\}$ parametrizes positions where operators don't collide. Its compactification $\overline{C}_n(X)$ adds boundary divisors $D_{ij} = \{z_i = z_j\}$ that encode collision limits. A deformation of the chiral algebra must specify how the algebraic structure changes as points approach these divisors.

\section{Construction of the Chiral Hochschild Complex}

\subsection{The Cochain Spaces}

\begin{definition}[Chiral Hochschild Complex - Geometric Realization]
For a chiral algebra $\mathcal{A}$ on a smooth curve $X$, define the degree $n$ cochains as
\[
C^n_{\text{chiral}}(\mathcal{A}) = \Gamma\left(\overline{C}_{n+2}(X), j_*j^*\mathcal{A}^{\boxtimes (n+2)} \otimes \Omega^n_{\overline{C}_{n+2}(X)}(\log D)\right)
\]
where:
\begin{itemize}
\item $\overline{C}_{n+2}(X)$ is the Fulton-MacPherson compactification
\item $j: C_{n+2}(X) \to \overline{C}_{n+2}(X)$ is the open embedding
\item $\mathcal{A}^{\boxtimes (n+2)}$ denotes the external tensor product on $X^{n+2}$
\item $\Omega^n_{\overline{C}_{n+2}(X)}(\log D)$ are $n$-forms with logarithmic poles along the boundary divisor $D$
\end{itemize}
\end{definition}

The index $n+2$ (rather than $n$) appears because Hochschild cohomology involves one output, $n$ inputs, and one evaluation point. Explicitly, a degree $n$ cochain is a sum of expressions
\[
\phi = \sum_I a_0^{(I)}(z_0) \otimes a_1^{(I)}(z_1) \otimes \cdots \otimes a_n^{(I)}(z_n) \otimes a_{\infty}^{(I)}(z_{\infty}) \otimes \omega_I
\]
where $a_i^{(I)} \in \mathcal{A}$ and $\omega_I$ is an $n$-form on $\overline{C}_{n+2}(X)$ with logarithmic singularities.

\subsection{The Differential: Three Components United}

The differential $d: C^n_{\text{chiral}} \to C^{n+1}_{\text{chiral}}$ has three components reflecting the algebraic, geometric, and operadic structures:

\begin{theorem}[The Chiral Hochschild Differential]
The differential decomposes as
\[
d = d_{\text{int}} + d_{\text{fact}} + d_{\text{config}}
\]
where:
\begin{enumerate}
\item $d_{\text{int}}$: internal differential from the $\mathcal{D}_X$-module structure
\item $d_{\text{fact}}$: factorization using chiral multiplication  
\item $d_{\text{config}}$: de Rham differential on configuration space
\end{enumerate}
\end{theorem}

\begin{proof}
We verify $d^2 = 0$ by analyzing all nine combinations:

\textbf{Pure terms:}
\begin{align}
d_{\text{int}}^2 &= 0 \quad \text{($\mathcal{A}$ is a complex of $\mathcal{D}_X$-modules)} \\
d_{\text{config}}^2 &= 0 \quad \text{(de Rham differential squares to zero)} \\
d_{\text{fact}}^2 &= 0 \quad \text{(associativity of chiral multiplication)}
\end{align}

\textbf{Mixed terms:} The crucial cancellation 
\[
d_{\text{fact}} \circ d_{\text{config}} + d_{\text{config}} \circ d_{\text{fact}} = 0
\]
follows from the Arnold-Orlik-Solomon relations. For any configuration of three points:
\[
d\log(z_1-z_2) \wedge d\log(z_2-z_3) + d\log(z_2-z_3) \wedge d\log(z_3-z_1) + d\log(z_3-z_1) \wedge d\log(z_1-z_2) = 0
\]

This relation, discovered by Arnold \cite{Arn69} in studying configuration spaces of hyperplanes and generalized by Orlik-Solomon \cite{OS80}, encodes the fact that three points on a curve have only two degrees of freedom. Geometrically, it says the sum of exterior derivatives around a triangle vanishes.

The remaining mixed terms vanish because $d_{\text{int}}$ commutes with both other differentials by $\mathcal{D}_X$-linearity.
\end{proof}

\subsection{Explicit Formula for the Differential}

For a cochain $\phi \in C^n_{\text{chiral}}$, the differential acts by:

\begin{align}
(d_{\text{int}}\phi)(&z_0,\ldots,z_{n+1}) = \sum_{i=0}^{n+1} (-1)^i d_{\mathcal{A}}(\phi(z_0,\ldots,\hat{z}_i,\ldots,z_{n+1})) \\
(d_{\text{fact}}\phi)(&z_0,\ldots,z_{n+1}) = \sum_{i=1}^n (-1)^i \text{Res}_{z_i = z_0} \phi(\mu(z_0,z_i),z_1,\ldots,\hat{z}_i,\ldots,z_{n+1}) \\
&+ \sum_{1 \leq i < j \leq n} (-1)^{i+j} \phi(z_0,\ldots,\mu(z_i,z_j),\ldots,\hat{z}_i,\ldots,\hat{z}_j,\ldots,z_{n+1}) \\
(d_{\text{config}}\phi)(&z_0,\ldots,z_{n+1}) = d_{\overline{C}_{n+2}}(\phi)
\end{align}

where $\hat{z}_i$ denotes omission and $\mu$ is the chiral multiplication.

\section{Computing Cohomology via Bar-Cobar Resolution}

\subsection{The Resolution Strategy}

Computing Hochschild cohomology directly from the definition is typically intractable. The bar-cobar resolution provides a systematic approach:

\begin{theorem}[Hochschild via Bar-Cobar]
For any chiral algebra $\mathcal{A}$, there is a quasi-isomorphism
\[
C^{\bullet}_{\text{chiral}}(\mathcal{A}) \simeq \text{Hom}_{\text{ChirAlg}}(\Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A})), \mathcal{A})
\]
where $\Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A}))$ is the cobar construction of the bar complex.
\end{theorem}

\begin{proof}
The proof has three steps:

\textbf{Step 1: Bar gives cofree resolution.} 
The geometric bar complex $\overline{B}^{\text{ch}}(\mathcal{A})$ constructed in Chapter 4 is a cofree chiral coalgebra resolving $\mathcal{A}$:
\[
\overline{B}^{\text{ch}}(\mathcal{A}) \xrightarrow{\epsilon} \mathcal{A}
\]

\textbf{Step 2: Cobar gives free resolution.}
Applying the cobar functor (Chapter 5) yields a free chiral algebra resolution:
\[
\Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A})) \xrightarrow{\eta} \mathcal{A}
\]

\textbf{Step 3: Hom computes Ext.}
By definition, 
\[
\text{Ext}^n_{\text{ChirAlg}}(\mathcal{A}, \mathcal{A}) = H^n(\text{Hom}_{\text{ChirAlg}}(\Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A})), \mathcal{A}))
\]
The left side is precisely $HH^n_{\text{chiral}}(\mathcal{A})$ by definition.
\end{proof}

\subsection{The Spectral Sequence}

The double complex structure induces a spectral sequence:

\begin{theorem}[Hochschild Spectral Sequence]
There exists a spectral sequence
\[
E_2^{p,q} = H^p(\overline{C}_{q+2}(X), \mathcal{H}^q(\mathcal{A}^{\boxtimes (q+2)})) \Rightarrow HH^{p+q}_{\text{chiral}}(\mathcal{A})
\]
where $\mathcal{H}^q$ denotes the $q$-th cohomology sheaf.
\end{theorem}

For formal chiral algebras (quasi-isomorphic to their cohomology), this spectral sequence degenerates at $E_2$, giving:
\[
HH^n_{\text{chiral}}(\mathcal{A}) \cong \bigoplus_{p+q=n} H^p(\overline{C}_{q+2}(X), \mathcal{H}^q(\mathcal{A}^{\boxtimes (q+2)}))
\]

\section{Koszul Duality for Chiral Algebras}

\subsection{Quadratic Chiral Algebras and Their Duals}

\begin{definition}[Quadratic Chiral Algebra]
A chiral algebra $\mathcal{A}$ is \emph{quadratic} if it admits a presentation
\[
\mathcal{A} = T_{\text{chiral}}(\mathcal{V})/(R)
\]
where:
\begin{itemize}
\item $\mathcal{V}$ is a locally free $\mathcal{O}_X$-module of generators
\item $T_{\text{chiral}}(\mathcal{V})$ is the free chiral algebra on $\mathcal{V}$
\item $R \subset j_*j^*(\mathcal{V} \boxtimes \mathcal{V})$ consists of quadratic relations
\end{itemize}
\end{definition}

The free chiral algebra requires care to define. Following Beilinson-Drinfeld:

\begin{definition}[Free Chiral Algebra]
The free chiral algebra on $\mathcal{V}$ is
\[
T_{\text{chiral}}(\mathcal{V}) = \bigoplus_{n \geq 0} \pi_{n*}\left(j_*j^*\mathcal{V}^{\boxtimes n} \otimes \mathcal{D}_{C_n(X)/X}\right)^{\Sigma_n}
\]
where $\pi_n: C_n(X) \to X$ is the projection and $\mathcal{D}_{C_n(X)/X}$ denotes relative differential operators.
\end{definition}

\begin{definition}[Koszul Dual]
The Koszul dual of a quadratic chiral algebra $\mathcal{A}$ is
\[
\mathcal{A}^! = T_{\text{chiral}}(\mathcal{V}^*)/(R^{\perp})
\]
where:
\begin{itemize}
\item $\mathcal{V}^* = \mathcal{H}om_{\mathcal{O}_X}(\mathcal{V}, \omega_X)$ is the dual shifted by the canonical bundle
\item $R^{\perp}$ consists of relations orthogonal to $R$ under the canonical pairing
\[
\langle \cdot, \cdot \rangle: j_*j^*(\mathcal{V}^* \boxtimes \mathcal{V}) \to j_*\omega_{X^2 \setminus \Delta}
\]
\end{itemize}
\end{definition}

\begin{remark}[What This Definition Actually Says]\label{rem:koszul-dual-meaning}
The Koszul dual $\mathcal{A}^!$ defined above is \emph{precisely the coalgebra} that bar constructs from $\mathcal{A}$. More precisely:

\begin{enumerate}
\item \textbf{Generator duality}: The generators of $\mathcal{A}^!$ are the duals of the generators of $\mathcal{A}$:
   $$\mathcal{V}^* = \mathcal{H}om_{\mathcal{O}_X}(\mathcal{V}, \omega_X)$$
   This means: if $\mathcal{A}$ has generators $\phi_1, \ldots, \phi_n$, then $\mathcal{A}^!$ has dual generators $\phi_1^*, \ldots, \phi_n^*$

\item \textbf{Relation orthogonality}: The relations $R^{\perp}$ in $\mathcal{A}^!$ are orthogonal to the relations $R$ in $\mathcal{A}$ under the residue pairing:
   $$\langle r, r^* \rangle = \int_{X^2 \setminus \Delta} r \wedge r^* = 0 \quad \text{for all } r \in R, r^* \in R^{\perp}$$
   This means: what is a relation in $\mathcal{A}$ becomes "freedom" in $\mathcal{A}^!$, and vice versa

\item \textbf{Bar computes this dual}: The bar construction $\bar{B}^{\text{ch}}(\mathcal{A})$ naturally produces a coalgebra whose generators are $\mathcal{V}^*$ and whose coproduct encodes the relations $R^{\perp}$
\end{enumerate}

Therefore, saying $\bar{B}^{\text{ch}}(\mathcal{A}) \simeq \mathcal{A}^!$ is not a new condition but rather a \emph{verification} that the bar construction does what we expect: it produces the Koszul dual coalgebra.
\end{remark}

\begin{example}[Explicit Correspondence for Heisenberg]
For the Heisenberg chiral algebra $\mathcal{H}$ with generator $\alpha(z)$ and OPE:
$$\alpha(z)\alpha(w) \sim \frac{1}{(z-w)^2}$$

The Koszul dual $\mathcal{H}^!$ has:
\begin{itemize}
\item \textbf{Dual generator}: $\alpha^*(z)$ with $\langle \alpha, \alpha^* \rangle = 1$ under residue pairing
\item \textbf{Coproduct}: 
   $$\Delta(\alpha^*) = \alpha^* \otimes 1 + 1 \otimes \alpha^* + \text{(higher order terms)}$$
   encoding the dual of the commutative algebra structure
\item \textbf{Bar construction}: $\bar{B}^{\text{ch}}(\mathcal{H})$ consists of forms like:
   $$\alpha(z_1) \otimes \cdots \otimes \alpha(z_n) \otimes \eta_{12} \wedge \eta_{23} \wedge \cdots$$
   whose residues extract the coproduct coefficients
\end{itemize}

The cobar $\Omega^{\text{ch}}(\mathcal{H}^!)$ reconstructs a commutative chiral algebra from this coalgebraic data.
\end{example}

\begin{remark}[Why "Koszul Dual" vs "Dual"?]
The term "Koszul dual" (rather than just "dual") emphasizes that:
\begin{enumerate}
\item This is a derived/homotopical notion (quasi-isomorphisms, not isomorphisms)
\item It involves a specific homological construction (bar-cobar)
\item It generalizes the classical Koszul duality for quadratic algebras
\item The duality is self-inverse: $(\mathcal{A}^!)^! \simeq \mathcal{A}$
\end{enumerate}

When $\mathcal{A}$ is quadratic, $\mathcal{A}^!$ recovers the classical quadratic dual. For non-quadratic chiral algebras, $\mathcal{A}^!$ is defined by the bar construction but maintains all the essential dualities.
\end{remark}

\subsection{The Universal Twisting Morphism}

The relationship between a chiral algebra and its Koszul dual is mediated by:

\begin{definition}[Universal Twisting Morphism]
A \emph{twisting morphism} $\tau: \mathcal{A}^! \to \mathcal{A}$ is a degree 1 map satisfying the Maurer-Cartan equation
\[
\partial \tau + \tau \star \tau = 0
\]
where $\star$ denotes convolution in $\text{Hom}(\overline{B}^{\text{ch}}(\mathcal{A}^!), \Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A})))$.
\end{definition}

\begin{theorem}[Existence and Uniqueness]
For a Koszul pair $(\mathcal{A}, \mathcal{A}^!)$, there exists a unique universal twisting morphism $\tau: \mathcal{A}^! \to \mathcal{A}$ that induces quasi-isomorphisms:
\begin{align}
\mathcal{A}^!_{\tau} &\simeq \overline{B}^{\text{ch}}(\mathcal{A}) \\
\mathcal{A}_{\tau} &\simeq \Omega^{\text{ch}}(\mathcal{A}^!)
\end{align}
where the subscript denotes twisting by $\tau$.
\end{theorem}

\begin{remark}[What the Twisting Morphism Does]\label{rem:twisting-morphism-meaning}
The twisting morphism $\tau$ is the \textbf{explicit map implementing the bar-cobar isomorphism}. Concretely:

\begin{enumerate}
\item \textbf{Direction}: $\tau: \mathcal{A}^! \to \mathcal{A}$ is a map from the dual coalgebra to the original algebra

\item \textbf{Maurer-Cartan equation}: The condition $\partial \tau + \tau \star \tau = 0$ ensures that $\tau$ intertwines the coalgebra differential on $\mathcal{A}^!$ with the algebra differential on $\mathcal{A}$

\item \textbf{Twisted structures}: 
   \begin{itemize}
   \item $\mathcal{A}^!_{\tau}$ is $\mathcal{A}^!$ with differential twisted by $\tau$
   \item $\mathcal{A}_{\tau}$ is $\mathcal{A}$ with structure twisted by $\tau$
   \item The theorem says these twisted structures are quasi-isomorphic to bar and cobar
   \end{itemize}

\item \textbf{Universality}: $\tau$ is universal in that any other twisting factors through it
\end{enumerate}

Geometrically, $\tau$ is realized by:
$$\tau(c) = \int_{C_2(X)} \text{ev}^* c \wedge K_{\text{twist}}$$
where $K_{\text{twist}}$ is a universal integration kernel on the configuration space.
\end{remark}

\begin{example}[Twisting for Fermion-Boson Duality]
For the Koszul pair (free fermions $\mathcal{F}$, $\beta\gamma$ system $\mathcal{BG}$):

The twisting morphism $\tau: \mathcal{F}^! \to \mathcal{F}$ is given by:
$$\tau(\psi^*)(z) = \int_{\mathbb{C}} \psi(w) \cdot \frac{dw}{(z-w)}$$

This map:
\begin{itemize}
\item Takes the dual generator $\psi^*$ of $\mathcal{F}^!$
\item Integrates it against the fermion field $\psi$ with the basic kernel $\frac{1}{z-w}$
\item Produces a twisted field that satisfies bosonic commutation relations
\item Implements the fermion-boson correspondence at the level of Maurer-Cartan elements
\end{itemize}

The Maurer-Cartan equation $\partial \tau + \tau \star \tau = 0$ becomes the statement that this construction is consistent with the OPE structures on both sides.
\end{example}

\subsection{Main Duality Theorem}

\begin{theorem}[Koszul Duality for Hochschild Cohomology]
\label{thm:main-koszul-hoch}
For a Koszul pair $(\mathcal{A}, \mathcal{A}^!)$ of chiral algebras on a curve $X$:
\[
HH^n_{\text{chiral}}(\mathcal{A}) \cong HH^{2-n}_{\text{chiral}}(\mathcal{A}^!)^{\vee} \otimes \omega_X
\]
\end{theorem}

\begin{proof}[First Proof: Via Bar-Cobar Duality]
For Koszul algebras, the bar-cobar adjunction becomes an equivalence:
\[
\overline{B}^{\text{ch}}: \text{ChirAlg} \rightleftarrows \text{ChirCoalg}^{\text{op}}: \Omega^{\text{ch}}
\]

This gives isomorphisms:
\begin{align}
HH^n_{\text{chiral}}(\mathcal{A}) &= \text{Ext}^n_{\text{ChirAlg}}(\mathcal{A}, \mathcal{A}) \\
&\cong H^n(\text{Hom}(\Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A})), \mathcal{A})) \\
&\cong H^n(\text{Hom}(\mathcal{A}^!{}^{\text{¡}}, \mathcal{A}))
\end{align}

Using Poincaré-Verdier duality on configuration spaces:
\[
H^n(\overline{C}_m(X), \mathcal{F}) \cong H^{2m-2-n}(\overline{C}_m(X), \mathcal{F}^{\vee} \otimes \omega_{\overline{C}_m})^{\vee}
\]

Setting $m = n+2$ and $\mathcal{F} = \mathcal{A}^{\boxtimes (n+2)}$ yields the result.
\end{proof}

\begin{proof}[Second Proof: Via Twisting Morphism]
The universal twisting morphism $\tau: \mathcal{A}^! \to \mathcal{A}$ induces maps on Hochschild complexes:
\[
\tau_*: C^{\bullet}_{\text{chiral}}(\mathcal{A}^!) \to C^{\bullet}_{\text{chiral}}(\mathcal{A})
\]

For Koszul algebras, this is a quasi-isomorphism up to duality. The shift by 2 and twist by $\omega_X$ arise from:
\begin{itemize}
\item The degree shift in the definition of $\mathcal{A}^!$
\item The canonical bundle appearing in the duality pairing
\end{itemize}
\end{proof}

\section{Example: Complete Analysis of Boson-Fermion Duality}

\subsection{The Free Boson Chiral Algebra}

The free boson $\mathcal{B}$ on a curve $X$ is defined as follows:

\textbf{As a $\mathcal{D}_X$-module:}
\[
\mathcal{B} = \mathcal{D}_X / \mathcal{D}_X \cdot \partial^2
\]
This quotient makes $\mathcal{B}$ the sheaf of functions with pole of order at most 1.

\textbf{Generator:} The field $\alpha(z)$ generates $\mathcal{B}$ with conformal weight $h = 1$.

\textbf{Chiral multiplication:} Determined by the OPE
\[
\alpha(z_1) \alpha(z_2) = \frac{1}{(z_1-z_2)^2} + \text{regular}
\]

In terms of modes $\alpha(z) = \sum_{n \in \mathbb{Z}} \alpha_n z^{-n-1}$:
\[
[\alpha_m, \alpha_n] = m \delta_{m+n,0}
\]
This is the Heisenberg algebra with central charge $c = 1$.

\textbf{Vacuum representation:} The Fock space
\[
\mathcal{F}_{\mathcal{B}} = \mathbb{C}[\alpha_{-1}, \alpha_{-2}, \ldots] |0\rangle
\]
with $\alpha_n |0\rangle = 0$ for $n \geq 0$.

\subsection{The Free Fermion Chiral Algebra}

The free fermion $\mathcal{F}$ has:

\textbf{Generators:} Two fermionic fields $\psi(z), \psi^*(z)$ with $h = 1/2$.

\textbf{Relations:} The OPEs
\begin{align}
\psi(z_1)\psi^*(z_2) &= \frac{1}{z_1-z_2} + \text{regular} \\
\psi(z_1)\psi(z_2) &= 0 + \text{regular} \\
\psi^*(z_1)\psi^*(z_2) &= 0 + \text{regular}
\end{align}

In modes (half-integer for Neveu-Schwarz sector):
\begin{align}
\{\psi_r, \psi^*_s\} &= \delta_{r+s,0} \\
\{\psi_r, \psi_s\} &= 0 \\
\{\psi^*_r, \psi^*_s\} &= 0
\end{align}

\textbf{Fock space:}
\[
\mathcal{F}_{\mathcal{F}} = \Lambda^{\bullet}(\psi_{-1/2}, \psi_{-3/2}, \ldots, \psi^*_{-1/2}, \psi^*_{-3/2}, \ldots) |0\rangle
\]

\subsection{Establishing Koszul Duality}

\begin{theorem}[Boson-Fermion Koszul Duality]
The free boson and free fermion form a Koszul dual pair:
\[
\mathcal{B}^! \cong \mathcal{F}, \quad \mathcal{F}^! \cong \mathcal{B}
\]
\end{theorem}

\begin{proof}
We verify this at three levels:

\textbf{Level 1: Generators and Relations}

For $\mathcal{B}$:
\begin{itemize}
\item Generator space: $\mathcal{V}_{\mathcal{B}} = \mathcal{O}_X \cdot \alpha$ (one bosonic generator)
\item Relation space: $R_{\mathcal{B}} \subset j_*j^*(\mathcal{V}_{\mathcal{B}} \boxtimes \mathcal{V}_{\mathcal{B}})$ encodes the singular OPE
\end{itemize}

The dual has:
\begin{itemize}
\item $\mathcal{V}_{\mathcal{B}}^* = \omega_X \cdot \psi \oplus \omega_X \cdot \psi^*$ (two fermionic generators)
\item $R_{\mathcal{B}}^{\perp}$ gives the fermionic relations
\end{itemize}

The pairing 
\[
\langle \psi \otimes \psi^*, \alpha \otimes \alpha \rangle = \text{Res}_{z_1=z_2} \frac{dz_1 dz_2}{z_1-z_2} = 1
\]
is perfect, establishing the duality.

\textbf{Level 2: Bosonization}

The explicit isomorphism is given by bosonization:
\begin{align}
\psi(z) &= :e^{i\phi(z)}: \\
\psi^*(z) &= :e^{-i\phi(z)}: \\
\alpha(z) &= i\partial\phi(z)
\end{align}

where $\phi$ is the bosonic field with $\phi(z)\phi(w) \sim -\log(z-w)$.

This realizes the isomorphism at the level of vertex operators:
\[
Y_{\mathcal{F}}(\psi, z) = :e^{i\int^z \alpha}: \quad \text{(fermion as exponential of boson)}
\]

\textbf{Level 3: Bar-Cobar Verification}

Computing the bar complex:
\[
\overline{B}^{\text{ch}}(\mathcal{B}) = \text{span}\{[\alpha^{n_1}]|[\alpha^{n_2}]|\cdots|[\alpha^{n_k}]\}
\]

The coproduct:
\[
\Delta([\alpha^n]) = \sum_{i+j=n} [\alpha^i] \otimes [\alpha^j]
\]

This is precisely the coalgebra structure underlying $\mathcal{F}$.
\end{proof}

\subsection{Computing Hochschild Cohomology}

\begin{computation}[Boson Hochschild Cohomology]

\textbf{Degree 0:}
\[
HH^0_{\text{chiral}}(\mathcal{B}) = \text{End}_{\text{ChirAlg}}(\mathcal{B})
\]
An endomorphism $f: \mathcal{B} \to \mathcal{B}$ must preserve the OPE:
\[
f(\alpha(z))f(\alpha(w)) \sim \frac{1}{(z-w)^2}
\]
This forces $f(\alpha) = \lambda \alpha$ for $\lambda \in \mathbb{C}$. Thus $HH^0 = \mathbb{C}$.

\textbf{Degree 1:}
A derivation $D: \mathcal{B} \to \mathcal{B}$ must satisfy:
\[
D(\alpha(z)\alpha(w)) = D(\alpha(z))\alpha(w) + \alpha(z)D(\alpha(w))
\]
Using the OPE and comparing singularities, we find $D = 0$. Thus $HH^1 = 0$.

\textbf{Degree 2:}
A 2-cocycle $\phi \in C^2$ defines a deformation:
\[
\alpha(z) \cdot_t \alpha(w) = \alpha(z)\alpha(w) + t\phi(z,w)
\]
The cocycle condition ensures associativity to first order. The space of such deformations is one-dimensional, corresponding to the $\beta\gamma$ system:
\[
\beta(z)\gamma(w) \sim \frac{1}{z-w}, \quad \beta(z)\beta(w) \sim 0, \quad \gamma(z)\gamma(w) \sim \frac{\lambda}{(z-w)^2}
\]
Thus $HH^2 = \mathbb{C}$.
\end{computation}

\begin{computation}[Fermion Hochschild Cohomology]

By similar analysis:
\begin{align}
HH^0_{\text{chiral}}(\mathcal{F}) &= \mathbb{C} \quad \text{(scalars only)} \\
HH^1_{\text{chiral}}(\mathcal{F}) &= 0 \quad \text{(rigid)} \\
HH^2_{\text{chiral}}(\mathcal{F}) &= \mathbb{C} \quad \text{(deformation to interacting fermion)}
\end{align}
\end{computation}

\begin{verification}[Koszul Duality Check]
The duality theorem predicts:
\[
HH^n(\mathcal{B}) \cong HH^{2-n}(\mathcal{F})^{\vee}
\]
Indeed:
\begin{align}
HH^0(\mathcal{B}) = \mathbb{C} &\leftrightarrow HH^2(\mathcal{F})^{\vee} = \mathbb{C}^{\vee} = \mathbb{C} \\
HH^1(\mathcal{B}) = 0 &\leftrightarrow HH^1(\mathcal{F})^{\vee} = 0 \\
HH^2(\mathcal{B}) = \mathbb{C} &\leftrightarrow HH^0(\mathcal{F})^{\vee} = \mathbb{C}^{\vee} = \mathbb{C}
\end{align}
\end{verification}

\section{Classification of Periodicity Phenomena}

\subsection{Overview: Three Sources of Periodicity}

The Hochschild cohomology of chiral algebras can exhibit three distinct types of periodicity:

\begin{enumerate}
\item \textbf{Type I - Modular:} From rational central charge and modular transformations
\item \textbf{Type II - Quantum:} From quantum groups at roots of unity
\item \textbf{Type III - Geometric:} From topology of the underlying curve
\end{enumerate}

These three sources interact through the bar-cobar duality to produce complex periodicity patterns.

\subsection{Type I: Modular Periodicity from Rational Central Charge}

\subsubsection{The Mechanism}

When a chiral algebra has rational central charge $c = p/q$ with $\gcd(p,q) = 1$, modular transformations of the torus partition function create periodicity.

\begin{theorem}[Modular Periodicity]
Let $\mathcal{A}$ be a rational chiral algebra with central charge $c = p/q$. Then there exists $N | \text{lcm}(p,q,24)$ such that
\[
HH^{n+N}_{\text{chiral}}(\mathcal{A}) \cong HH^n_{\text{chiral}}(\mathcal{A}) \otimes M_N
\]
where $M_N$ is a module over the ring of modular forms of weight $N$.
\end{theorem}

\begin{proof}
The character of $\mathcal{A}$ transforms under $\tau \mapsto \tau + 1$ as:
\[
\text{ch}(\mathcal{A}, \tau+1) = e^{2\pi i c/24} \text{ch}(\mathcal{A}, \tau)
\]

For the transformation to return to itself, we need $e^{2\pi i cN/24} = 1$, which gives:
\[
N = \frac{24q}{\gcd(p,24)}
\]

This periodicity in the character induces periodicity in cohomology through the Euler-Poincaré principle:
\[
\sum_{n=0}^{\infty} (-1)^n \dim HH^n t^n = \text{ch}(\mathcal{A}, t)
\]

The generating function periodicity forces the cohomology dimensions to eventually repeat.
\end{proof}

\subsubsection{Examples}

\begin{example}[Minimal Models]
For Virasoro minimal models with 
\[
c = 1 - \frac{6(p-q)^2}{pq}
\]
where $\gcd(p,q) = 1$ and $p,q \geq 2$:

\begin{itemize}
\item Ising model $(p,q) = (3,4)$: $c = 1/2$, period divides 48
\item Tricritical Ising $(p,q) = (4,5)$: $c = 7/10$, period divides 240  
\item Three-state Potts $(p,q) = (5,6)$: $c = 4/5$, period divides 120
\end{itemize}
\end{example}

\begin{example}[WZW Models]
For $\widehat{\mathfrak{sl}}_2$ at level $k$:
\[
c = \frac{3k}{k+2}
\]
At $k=1$: $c = 1$, period 24 (related to $j$-invariant)
At $k=2$: $c = 3/2$, period 48
\end{example}

\subsubsection{Koszul Dual Behavior}

\begin{theorem}[Reflected Modular Periodicity]
If $\mathcal{A}$ has modular period $N$, its Koszul dual $\mathcal{A}^!$ has period $N'$ where:
\[
\frac{1}{N} + \frac{1}{N'} = \frac{1}{12}
\]
This reflects the duality of central charges in string theory: $c + c' = 26$ (bosonic) or $c + c' = 15$ (super).
\end{theorem}

\subsection{Type II: Quantum Group Periodicity}

\subsubsection{The Quantum Group Structure}

For affine Lie algebras at special levels, quantum groups at roots of unity emerge.

\begin{theorem}[Quantum Periodicity]
Let $\mathcal{W}^k(\mathfrak{g})$ be the W-algebra at level $k = -h^{\vee} + p/q$ where $h^{\vee}$ is the dual Coxeter number. Then:
\[
HH^{n+M}_{\text{chiral}}(\mathcal{W}^k(\mathfrak{g})) \cong HH^n_{\text{chiral}}(\mathcal{W}^k(\mathfrak{g}))
\]
where $M = 2h^{\vee}pq/\gcd(p,q,h^{\vee})$.
\end{theorem}

\begin{proof}
At these levels, the quantum group $U_q(\mathfrak{g})$ with $q = \exp(2\pi i/(h^{\vee} + k))$ has:

\textbf{1. Finite-dimensional center:} The center $Z(U_q)$ is spanned by $\{g^p : p | \text{order}(q)\}$.

\textbf{2. Periodic quantum dimensions:} The quantum integers
\[
[n]_q = \frac{q^n - q^{-n}}{q - q^{-1}}
\]
are periodic in $n$ with period $2\cdot\text{order}(q)$.

\textbf{3. Finite fusion rules:} The tensor product of representations closes on a finite set.

These force the bar complex to have periodic homology, which translates to periodic Hochschild cohomology.
\end{proof}

\subsubsection{Concrete Computation}

\begin{algorithm}
\caption{Computing Quantum Period}
\begin{verbatim}
def compute_quantum_period(g, k):
    """
    Compute period from quantum group at level k
    
    Args:
        g: Simple Lie algebra
        k: Level (rational)
    
    Returns:
        Period of Hochschild cohomology
    """
    h_dual = dual_coxeter_number(g)
    
    # Write k = -h_dual + p/q
    p, q = (k + h_dual).as_rational()
    
    # Quantum parameter
    q_param = exp(2*pi*i*q/(p*h_dual))
    
    # Find order of q_param
    order = 1
    q_power = q_param
    while abs(q_power - 1) > 1e-10:
        q_power *= q_param
        order += 1
        if order > 1000:
            return None  # Not periodic
    
    # Period is 2 * order for quantum dimensions
    return 2 * order

# Example: sl_2 at level -2 + 1/n
for n in [2, 3, 4, 5]:
    k = -2 + Rational(1, n)
    period = compute_quantum_period('sl_2', k)
    print(f"Level {k}: Period {period}")
\end{verbatim}
\end{algorithm}

\subsubsection{Physical Interpretation}

In CFT, this periodicity corresponds to:
\begin{itemize}
\item Fusion rules closing on finite set (rational CFT)
\item Verlinde formula giving integer fusion coefficients
\item Modular S-matrix having finite order
\end{itemize}

\subsection{Type III: Geometric Periodicity from Higher Genus}

\subsubsection{Genus Dependence}

On a genus $g > 0$ curve, new sources of periodicity arise:

\begin{theorem}[Geometric Periodicity]
For a chiral algebra $\mathcal{A}$ on a genus $g$ curve $X$:
\[
\text{Period}_{\text{geom}} | \text{lcm}(12(2g-2), |\text{Tors}(\text{Jac}(X))|, |\text{Tors}(\text{Pic}^0(X))|)
\]
\end{theorem}

\begin{proof}
Three geometric sources contribute:

\textbf{1. Canonical bundle:} $K_X^{\otimes n} = \mathcal{O}_X$ iff $n | 2g-2$ (except $g=1$).

\textbf{2. Torsion in Jacobian:} Points of finite order in $\text{Jac}(X)$ create monodromy.

\textbf{3. Flat line bundles:} Characters of $\pi_1(X)$ give finite group action.

Each contributes to periodicity through:
\[
HH^n(\mathcal{A}) = \bigoplus_{\chi} H^n(\overline{C}_{n+2}(X), \mathcal{L}_{\chi})
\]
where $\mathcal{L}_{\chi}$ are flat line bundles labeled by characters.
\end{proof}

\subsubsection{Examples at Different Genera}

\begin{example}[Genus 0 - Sphere]
No geometric periodicity (simply connected, no moduli).
\end{example}

\begin{example}[Genus 1 - Torus]
For elliptic curve $E_{\tau}$:
\begin{itemize}
\item Period lattice $\Lambda = \mathbb{Z} + \tau\mathbb{Z}$
\item Four spin structures (fermions have period 8)
\item Modular parameter $\tau$ gives $SL_2(\mathbb{Z})$ action
\end{itemize}

Free fermion on $E_{\tau}$:
\[
HH^{n+8}(\mathcal{F}, E_{\tau}) \cong HH^n(\mathcal{F}, E_{\tau})
\]
The period 8 comes from: 4 spin structures × 2 (fermion parity).
\end{example}

\begin{example}[Genus 2]
Hyperelliptic curve with 16 spin structures:
\begin{itemize}
\item Canonical divisor has degree $2g-2 = 2$
\item Period matrix is $2 \times 2$ (4 real parameters)
\item Jacobian typically has large torsion
\end{itemize}
\end{example}

\subsection{Unified Periodicity Theorem}

\begin{theorem}[Complete Periodicity Classification]
For a chiral algebra $\mathcal{A}$ on genus $g$ curve with central charge $c = p/q$ and quantum group level inducing period $M$:
\[
\text{Period}(\mathcal{A}) | \text{lcm}(N_{\text{modular}}, N_{\text{quantum}}, N_{\text{geometric}})
\]
where:
\begin{align}
N_{\text{modular}} &= \text{lcm}(p, q, 24) \\
N_{\text{quantum}} &= M \text{ (from quantum group)} \\
N_{\text{geometric}} &= \text{lcm}(12(2g-2), |\text{Tors}(\text{Jac}(X))|)
\end{align}
\end{theorem}

\begin{proof}
The three sources act independently on different parts of the spectral sequence:
\[
E_2^{p,q} = H^p(\overline{C}_{q+2}(X)) \otimes H^q(\mathcal{A}^{\otimes(q+2)})
\]
\begin{itemize}
\item Modular periodicity affects the second factor through representation theory
\item Quantum periodicity affects fusion rules and tensor products
\item Geometric periodicity affects the first factor through topology
\end{itemize}

Since they act on orthogonal components, the total period is their lcm.
\end{proof}

\subsection{Koszul Duality and Periodicity Interaction}

\begin{theorem}[Periodicity Exchange under Koszul Duality]
Let $(\mathcal{A}, \mathcal{A}^!)$ be a Koszul dual pair. If $\mathcal{A}$ has period decomposition:
\[
N_{\mathcal{A}} = N_{\text{mod}} \cdot N_{\text{quant}} \cdot N_{\text{geom}}
\]
Then $\mathcal{A}^!$ has period:
\[
N_{\mathcal{A}^!} = N'_{\text{mod}} \cdot N_{\text{quant}} \cdot N_{\text{geom}}
\]
where $N'_{\text{mod}}$ satisfies the harmonic mean relation:
\[
\frac{1}{N_{\text{mod}}} + \frac{1}{N'_{\text{mod}}} = \frac{1}{12}
\]
\end{theorem}

This shows:
\begin{itemize}
\item Modular periodicity exchanges harmonically (boson $\leftrightarrow$ fermion)
\item Quantum periodicity is preserved (same quantum group)
\item Geometric periodicity is unchanged (same underlying curve)
\end{itemize}

\section{Computational Methods and Algorithms}

\subsection{Direct Computation via Spectral Sequence}

\begin{algorithm}
\caption{Hochschild via Spectral Sequence}
\begin{verbatim}
class HochschildSpectralSequence:
    """
    Compute chiral Hochschild cohomology via spectral sequence
    """
    
    def __init__(self, chiral_algebra, curve):
        self.A = chiral_algebra
        self.X = curve
        self.FM = FultonMacPhersonSpace(curve)
        
    def E1_page(self, p, q):
        """
        E_1^{p,q} = H^p(C_{q+2}, A^{⊗(q+2)})
        """
        config_space = self.FM.get_space(q + 2)
        A_tensor = self.A.tensor_power(q + 2)
        
        # Compute via Cech cohomology
        cover = config_space.good_cover()
        cech_complex = CechComplex(cover, A_tensor)
        return cech_complex.cohomology(p)
    
    def differential_d1(self, p, q):
        """
        d_1: E_1^{p,q} → E_1^{p+1,q}
        
        Induced by bar differential
        """
        source = self.E1_page(p, q)
        target = self.E1_page(p + 1, q)
        
        # Use residue maps
        d = Matrix(target.dimension(), source.dimension())
        
        for i, divisor in enumerate(self.FM.boundary_divisors(q + 2)):
            # Residue along divisor
            res_map = self.residue_map(divisor, p, q)
            d += (-1)**i * res_map
            
        return d
    
    def E2_page(self, p, q):
        """
        E_2^{p,q} = Ker(d_1) / Im(d_1)
        """
        d_in = self.differential_d1(p - 1, q)
        d_out = self.differential_d1(p, q)
        
        ker = d_out.kernel()
        im = d_in.image()
        
        return ker.quotient(im)
    
    def converges_at_E2(self):
        """
        Check if spectral sequence degenerates at E_2
        
        True for formal chiral algebras
        """
        return self.A.is_formal()
    
    def hochschild_cohomology(self, n):
        """
        Compute HH^n by summing over E_∞^{p,q} with p+q=n
        """
        if self.converges_at_E2():
            # Direct sum
            HH_n = VectorSpace(0)
            for p in range(n + 1):
                q = n - p
                HH_n = HH_n.direct_sum(self.E2_page(p, q))
            return HH_n
        else:
            # Need higher differentials
            return self.compute_E_infinity(n)
\end{verbatim}
\end{algorithm}

\subsection{Computation via Bar-Cobar Resolution}

\begin{algorithm}
\caption{Bar-Cobar Method}
\begin{verbatim}
def hochschild_via_bar_cobar(A, max_degree=5):
    """
    Compute HH^*_chiral(A) using bar-cobar resolution
    
    Strategy:
    1. Build bar complex B(A)
    2. Apply cobar to get Ω(B(A))  
    3. Compute Hom(Ω(B(A)), A)
    4. Take cohomology
    """
    
    # Step 1: Bar complex
    print("Constructing bar complex...")
    bar = BarComplex(A)
    
    for n in range(max_degree + 2):
        # Bar^n has basis from tensor products
        bar[n] = construct_bar_level(A, n)
        print(f"  Bar^{n}: dimension {bar[n].dimension()}")
    
    # Step 2: Cobar complex
    print("\nApplying cobar functor...")
    cobar = CobarComplex(bar)
    
    # For Koszul algebras, cobar gives the dual
    if A.is_koszul():
        print("  Koszul algebra detected!")
        cobar = A.koszul_dual().twisted_complex()
    
    # Step 3: Hom complex
    print("\nConstructing Hom complex...")
    hom_complex = []
    
    for n in range(max_degree + 1):
        # Hom in degree n
        hom_n = HomSpace(cobar[n], A)
        hom_complex.append(hom_n)
        print(f"  Hom^{n}: dimension {hom_n.dimension()}")
    
    # Step 4: Compute cohomology
    print("\nComputing cohomology...")
    hochschild = {}
    
    for n in range(max_degree):
        # Differential
        if n > 0:
            d_in = hom_differential(hom_complex[n-1], hom_complex[n])
        else:
            d_in = None
            
        if n < max_degree - 1:
            d_out = hom_differential(hom_complex[n], hom_complex[n+1])
        else:
            d_out = None
        
        # Cohomology
        if d_in is None:
            ker = hom_complex[0]
        else:
            ker = d_out.kernel() if d_out else hom_complex[n]
            
        if d_in is None:
            im = VectorSpace(0)
        else:
            im = d_in.image()
        
        hochschild[n] = ker.quotient(im)
        print(f"  HH^{n}: dimension {hochschild[n].dimension()}")
    
    return hochschild

def construct_bar_level(A, n):
    """
    Construct Bar^n(A) geometrically
    """
    # Configuration space
    curve = A.base_curve()
    FM = FultonMacPherson(curve, n + 1)
    
    # Logarithmic forms
    log_forms = []
    for divisor in FM.boundary_divisors():
        # d log(z_i - z_j) form
        eta = LogarithmicForm(divisor)
        log_forms.append(eta)
    
    # Tensor with algebra
    A_tensor = A.tensor_power(n + 1)
    
    # Global sections
    return GlobalSections(FM, A_tensor.tensor(ExteriorAlgebra(log_forms)))
\end{verbatim}
\end{algorithm}

\subsection{Detecting Periodicity}

\begin{algorithm}
\caption{Periodicity Detection}
\begin{verbatim}
def detect_periodicity(A, max_check=100, confidence=0.99):
    """
    Detect periodicity in Hochschild cohomology
    
    Returns:
        (period, type, confidence_score)
    """
    
    # Compute dimensions
    dims = []
    for n in range(max_check):
        HH_n = hochschild_via_bar_cobar(A, max_degree=n+1)[n]
        dims.append(HH_n.dimension())
        print(f"dim HH^{n} = {dims[-1]}")
    
    # Method 1: Autocorrelation
    def autocorrelation(period):
        if period >= len(dims) // 2:
            return 0
        
        matches = 0
        total = 0
        for i in range(len(dims) - period):
            if dims[i] == dims[i + period]:
                matches += 1
            total += 1
        
        return matches / total if total > 0 else 0
    
    # Find best period
    best_period = 1
    best_score = 0
    
    for p in range(1, len(dims) // 2):
        score = autocorrelation(p)
        if score > best_score:
            best_score = score
            best_period = p
    
    # Method 2: Check theoretical predictions
    predictions = []
    
    # Modular periodicity
    if A.central_charge().is_rational():
        c = A.central_charge()
        p, q = c.numerator(), c.denominator()
        N_mod = lcm(p, q, 24)
        predictions.append(('modular', N_mod))
    
    # Quantum periodicity  
    if hasattr(A, 'quantum_group_level'):
        k = A.quantum_group_level()
        if k.is_rational():
            # Compute quantum period
            N_quantum = compute_quantum_period(A.lie_algebra(), k)
            predictions.append(('quantum', N_quantum))
    
    # Geometric periodicity
    g = A.base_curve().genus()
    if g > 0:
        N_geom = 12 * (2*g - 2) if g > 1 else 12
        predictions.append(('geometric', N_geom))
    
    # Check which prediction matches
    for pred_type, pred_period in predictions:
        if best_period == pred_period or best_period | pred_period:
            return (pred_period, pred_type, best_score)
    
    # Return empirical result
    return (best_period, 'empirical', best_score)

# Example usage
A = FreeBoson()
period, period_type, confidence = detect_periodicity(A)
print(f"\nDetected period {period} of type '{period_type}' with confidence {confidence:.2f}")
\end{verbatim}
\end{algorithm}

\section{Physical Applications}

\subsection{Marginal Deformations in CFT}

In 2D conformal field theory, $HH^2_{\text{chiral}}(\mathcal{A})$ classifies marginal deformations of the action:
\[
S \to S + \lambda \int_{\Sigma} \phi(z,\bar{z}) d^2z
\]

The deformation preserves conformal invariance iff:
\begin{itemize}
\item $\phi$ has conformal weight $(1,1)$ (marginality)
\item $[\phi] \in HH^2_{\text{chiral}}$ is a cocycle (preserves OPE algebra)
\item Obstruction in $HH^3_{\text{chiral}}$ vanishes (extends to all orders)
\end{itemize}

\begin{example}[Exactly Marginal Deformations]
\begin{itemize}
\item Free boson: $HH^2 = \mathbb{C}$ gives radius deformation
\item $\mathcal{N}=4$ SYM: $HH^2 = \mathbb{C}^{3(g-1)}$ gives gauge coupling and theta angles
\item Minimal models: $HH^2 = 0$ (isolated in moduli space)
\end{itemize}
\end{example}

\subsection{String Field Theory}

The $A_{\infty}$ structure encoded in Hochschild cohomology gives string field theory vertices:

\begin{theorem}[String Field Theory from Hochschild]
The operations $m_n: \mathcal{A}^{\otimes n} \to \mathcal{A}[2-n]$ extracted from $HH^{\bullet}_{\text{chiral}}$ satisfy:
\[
\sum_{i+j=n+1} \sum_{k} (-1)^{ik+j} m_i(id^{\otimes k} \otimes m_j \otimes id^{\otimes(i-k-1)}) = 0
\]
These give:
\begin{itemize}
\item $m_1$: BRST operator $Q$
\item $m_2$: String multiplication
\item $m_3$: Four-string vertex
\item Higher $m_n$: Contact terms
\end{itemize}
\end{theorem}

The action:
\[
S[\Psi] = \frac{1}{2}\langle \Psi, Q\Psi \rangle + \sum_{n \geq 3} \frac{1}{n!}\langle \Psi, m_n(\Psi,\ldots,\Psi)\rangle
\]

\subsection{Holographic Duality}

Koszul duality of chiral algebras provides a mathematical framework for holography:

\begin{conjecture}[Holographic Koszul Duality]
The AdS$_3$/CFT$_2$ correspondence exchanges:
\begin{itemize}
\item Bulk gravity ↔ Boundary CFT
\item Boson-like fields ↔ Fermion-like fields  
\item $\mathcal{A}_{\text{bulk}}^! \cong \mathcal{A}_{\text{boundary}}$
\end{itemize}
\end{conjecture}

Evidence:
\begin{itemize}
\item Central charges add: $c_{\text{bulk}} + c_{\text{boundary}} = 26$
\item Hochschild cohomologies are Koszul dual
\item Twisting morphism encodes holographic dictionary
\end{itemize}

\section{Conclusions and Future Directions}

\subsection{Summary of Results}

We have established:

\begin{enumerate}
\item \textbf{Complete geometric construction} of chiral Hochschild cohomology via configuration spaces

\item \textbf{Koszul duality theorem} exchanging $HH^n(\mathcal{A}) \cong HH^{2-n}(\mathcal{A}^!)^{\vee}$

\item \textbf{Classification of periodicity}:
   \begin{itemize}
   \item Type I: Modular (rational CFT)
   \item Type II: Quantum (roots of unity)
   \item Type III: Geometric (higher genus)
   \end{itemize}

\item \textbf{Computational algorithms} for practical calculations

\item \textbf{Physical applications} to CFT deformations and string theory
\end{enumerate}

\subsection{Open Problems}

\begin{enumerate}
\item \textbf{Continuous cohomology:} Can we define $HH^{\alpha}$ for $\alpha \in \mathbb{R}$?

\item \textbf{Derived enhancement:} Extend to derived chiral algebras

\item \textbf{Categorification:} Lift to factorization homology

\item \textbf{4d/2d correspondence:} Relate to cohomology of 4d gauge theories

\item \textbf{Quantum groups:} Fully understand periodicity from quantum groups
\end{enumerate}

\subsection{The Path to Continuous Cohomology}

The periodicity phenomena suggest a deeper structure: continuous families of cohomology theories interpolating between discrete degrees. The three types of periodicity could be unified by:
\begin{itemize}
\item Replacing $\mathbb{Z}$-grading with $\mathbb{R}$-grading
\item Using spectral flow operators to interpolate
\item Employing $L^2$ methods on infinite-dimensional spaces
\end{itemize}

This points toward the continuous cohomology theories originally envisioned, where the discrete scaffold of Hochschild cohomology extends to a continuous spectrum.
\section{Computing Hochschild Cohomology via Bar-Cobar Resolution}
\label{sec:hochschild-via-bar-cobar-complete}

We now use the geometric bar-cobar construction to compute Hochschild cohomology
of chiral algebras explicitly. This approach has three major advantages:
\begin{enumerate}
\item \textbf{Geometric}: Realizes HH* as cohomology of configuration spaces
\item \textbf{Computational}: Provides explicit formulas for all degrees
\item \textbf{Structural}: Reveals hidden operations (Gerstenhaber bracket, L∞ structure)
\end{enumerate}

\subsection{The Bar-Cobar Resolution Strategy}

\begin{strategy}[Why Bar-Cobar?]\label{strategy:bar-cobar-resolution}
Computing Hochschild cohomology directly from the definition:
$$HH^n(\mathcal{A}) = \text{Ext}^n_{\mathcal{A}^e}(\mathcal{A}, \mathcal{A})$$

requires finding projective resolutions of $\mathcal{A}$ as an $\mathcal{A}^e$-module.
This is generally intractable.

\textbf{Bar-cobar approach:}
\begin{enumerate}
\item The \textbf{bar complex} $\bar{B}(\mathcal{A})$ is a \emph{cofree} coalgebra resolution
of $\mathcal{A}$
\item The \textbf{cobar complex} $\Omega(\bar{B}(\mathcal{A}))$ is a \emph{free} algebra
resolution of $\mathcal{A}$
\item Therefore:
$$HH^n(\mathcal{A}) = H^n(\text{Hom}_{\mathsf{Alg}}(\Omega(\bar{B}(\mathcal{A})), \mathcal{A}))$$
\end{enumerate}

The geometric realization makes all of this completely explicit.
\end{strategy}

\subsection{The Fundamental Quasi-Isomorphism}

\begin{theorem}[Bar-Cobar Resolution]\label{thm:bar-cobar-resolution}
For any chiral algebra $\mathcal{A}$ on a curve $X$, there is a quasi-isomorphism:
$$\Omega^{\text{geom}}(\bar{B}^{\text{geom}}(\mathcal{A})) \xrightarrow{\sim} \mathcal{A}$$

This means the cobar-of-bar complex is a \textbf{free resolution} of $\mathcal{A}$.
\end{theorem}

\begin{proof}[Proof Strategy]
\textbf{Step 1: Bar is a cofree resolution.}

The bar complex $\bar{B}^{\text{geom}}(\mathcal{A})$ is constructed as:
$$\bar{B}^n = \Gamma(\overline{C}_{n+1}(X), \mathcal{A}^{\boxtimes n+1} \otimes \Omega^n(\log D))$$

with differential $d = d_{\text{internal}} + d_{\text{residue}} + d_{\text{form}}$
satisfying $d^2 = 0$.

The augmentation map:
$$\epsilon: \bar{B}^0 = \mathcal{A} \to \mathcal{A}, \quad \epsilon(\phi) = \phi$$

makes this a resolution: the homology $H_*(\bar{B}, d)$ is concentrated in degree 0 and
equals $\mathcal{A}$.

\textbf{Step 2: Cobar gives free resolution.}

Applying the cobar functor $\Omega^{\text{geom}}$ to $\bar{B}(\mathcal{A})$
gives a complex of \emph{distributions} with differential inserting delta functions.

The cobar complex is \emph{free} as an algebra (it's freely generated by cobar generators).

\textbf{Step 3: Quasi-isomorphism.}

The composite:
$$\Omega(\bar{B}(\mathcal{A})) \xrightarrow{\epsilon_{\text{cobar}}} \mathcal{A}$$

is defined by ``evaluating at the identity'': $\epsilon_{\text{cobar}}(K) = \langle K, \text{id} \rangle$.

\textbf{Key lemma:} This is a quasi-isomorphism, meaning it induces isomorphisms on homology:
$$H^*(\Omega(\bar{B}(\mathcal{A})), d_{\text{cobar}}) \xrightarrow{\sim} H^*(\mathcal{A}, d_{\mathcal{A}})$$

For chiral algebras with no higher cohomology (like Heisenberg, free boson/fermion), the
right side is just $\mathcal{A}$ itself in degree 0.

\textbf{Conclusion:} $\Omega(\bar{B}(\mathcal{A}))$ is a free resolution of $\mathcal{A}$,
allowing us to compute Ext groups.
\qed
\end{proof}

\begin{remark}[Why This Works]
The bar-cobar construction ``undoes itself'':
\begin{align*}
\mathcal{A} &\xrightarrow{\bar{B}} \text{Coalgebra (with boundaries)}\\
&\xrightarrow{\Omega} \text{Algebra (with singularities)}\\
&\xrightarrow{\epsilon} \mathcal{A} \quad \text{(back to original)}
\end{align*}

The composition $\epsilon \circ \Omega \circ \bar{B}$ is homotopic to the identity, giving
the resolution.
\end{remark}

\subsection{Hochschild Cohomology Formula}

\begin{theorem}[HH* via Configuration Spaces]\label{thm:HH-config-space-formula}
The Hochschild cohomology of a chiral algebra $\mathcal{A}$ is computed by:
$$HH^n_{\text{chiral}}(\mathcal{A}) = H^n\left(\Gamma\left(\overline{C}_{n+2}(X), 
\text{Hom}_{\mathcal{D}_X}(\mathcal{A}^{\boxtimes n+2}, \mathcal{A}) \otimes \Omega^n(\log D)\right), d_{\text{Hoch}}\right)$$

where the Hochschild differential $d_{\text{Hoch}}$ has three components:
\begin{align}
d_{\text{Hoch}} &= d_{\text{internal}} + d_{\text{factor}} + d_{\text{form}} \label{eq:d-Hoch-decomposition}
\end{align}

\textbf{Component descriptions:}
\begin{enumerate}
\item $d_{\text{internal}}$: Internal differential on $\mathcal{A}$-factors
\item $d_{\text{factor}}$: Factorization using chiral product (OPE collisions)
\item $d_{\text{form}}$: de Rham differential on configuration space forms
\end{enumerate}
\end{theorem}

\begin{proof}
\textbf{Step 1: Definition of Hochschild cochains.}

By definition:
$$C^n_{\text{Hoch}}(\mathcal{A}) = \text{Hom}_{\mathcal{A}^e}(\mathcal{A}^{\otimes n+2}, \mathcal{A})$$

An $\mathcal{A}^e$-linear map must commute with the bimodule structure, which for chiral
algebras means:
\begin{itemize}
\item Commutes with $\mathcal{D}_X$-module structure
\item Respects locality (support properties)
\item Compatible with chiral products
\end{itemize}

\textbf{Step 2: Geometric realization.}

Such maps are naturally parametrized by configuration spaces: a Hochschild $n$-cochain
assigns to each configuration of $n+2$ points a multilinear map.

Explicitly, $f \in C^n_{\text{Hoch}}$ corresponds to a section:
$$f \in \Gamma(\overline{C}_{n+2}(X), \text{Hom}(\mathcal{A}^{\boxtimes n+2}, \mathcal{A}) 
\otimes \Omega^n(\log D))$$

The logarithmic forms account for the singular behavior as points collide.

\textbf{Step 3: Differential.}

The Hochschild differential is:
$$(df)(a_0, \ldots, a_{n+1}) = \mu(a_0, f(a_1, \ldots, a_{n+1})) + \sum_{i=1}^n (-1)^i 
f(a_0, \ldots, \mu(a_i, a_{i+1}), \ldots, a_{n+1}) + (-1)^{n+1} \mu(f(a_0, \ldots, a_n), a_{n+1})$$

Geometrically, each term corresponds to:
\begin{itemize}
\item First term: factorization at boundary (first two points collide)
\item Middle terms: factorization at interior points  
\item Last term: factorization at opposite boundary
\end{itemize}

Combined with the de Rham differential on forms, we get $d_{\text{Hoch}}$ as described.
\qed
\end{proof}

\begin{remark}[Three Components Explained]
The decomposition \eqref{eq:d-Hoch-decomposition} mirrors the bar differential:

\begin{center}
\begin{tabular}{c|c|c}
\textbf{Bar} & \textbf{Hochschild} & \textbf{Meaning} \\
\hline
$d_{\text{internal}}$ & $d_{\text{internal}}$ & Differential on $\mathcal{A}$ \\
$d_{\text{residue}}$ & $d_{\text{factor}}$ & Extract boundary data \\
$d_{\text{form}}$ & $d_{\text{form}}$ & Configuration space geometry \\
\end{tabular}
\end{center}

This parallel is not coincidental: it reflects the deep connection between bar complex
and Hochschild complex via the Ext definition.
\end{remark}

\subsection{Explicit Computation: Free Boson (Heisenberg Algebra)}

\begin{example}[Hochschild of Heisenberg - Complete]\label{ex:HH-heisenberg-complete}
For the free boson $\mathcal{B}$ (Heisenberg chiral algebra) with field $\alpha(z)$ and OPE:
$$\alpha(z_1)\alpha(z_2) \sim \frac{k}{(z_1 - z_2)^2}$$

We compute all Hochschild cohomology groups.

\subsubsection{Degree 0: $HH^0(\mathcal{B})$}

$$HH^0 = \text{End}_{\mathsf{ChirAlg}}(\mathcal{B}) = \{f: \mathcal{B} \to \mathcal{B} 
\text{ preserving OPE}\}$$

Any such endomorphism must satisfy:
$$f(\alpha(z_1))f(\alpha(z_2)) \sim \frac{k}{(z_1-z_2)^2}$$

Since $\alpha$ is the unique generator (up to scaling), we must have $f(\alpha) = \lambda \alpha$
for $\lambda \in \mathbb{C}$.

But the OPE coefficient must match:
$$\lambda^2 \cdot \frac{k}{(z_1-z_2)^2} = \frac{k}{(z_1-z_2)^2} \implies \lambda^2 = 1 \implies \lambda = \pm 1$$

By conventions (positivity), $\lambda = 1$.

$$\boxed{HH^0(\mathcal{B}) = \mathbb{C}}$$

\subsubsection{Degree 1: $HH^1(\mathcal{B})$}

$$HH^1 = \text{Der}(\mathcal{B}) = \{D: \mathcal{B} \to \mathcal{B} \text{ derivation}\}$$

A derivation satisfies:
$$D(\alpha(z_1)\alpha(z_2)) = D(\alpha(z_1))\alpha(z_2) + \alpha(z_1)D(\alpha(z_2))$$

Using the OPE $\alpha \times \alpha \sim k/(z_1-z_2)^2$:
$$D\left(\frac{k}{(z_1-z_2)^2}\right) = \frac{D(\alpha)(z_1) \alpha(z_2) + \alpha(z_1)D(\alpha)(z_2)}{(z_1-z_2)^2}$$

The left side is a $c$-number (no field dependence), while the right side has field
dependence unless $D(\alpha) = 0$.

Therefore: $D = 0$.

$$\boxed{HH^1(\mathcal{B}) = 0}$$

\subsubsection{Degree 2: $HH^2(\mathcal{B})$}

$HH^2$ classifies deformations of the chiral algebra structure.

A deformation is given by modifying the OPE:
$$\alpha(z_1) \times_t \alpha(z_2) = \alpha(z_1)\alpha(z_2) + t \cdot \phi(z_1, z_2) + O(t^2)$$

where $\phi$ is a 2-cocycle.

\textbf{Cocycle condition:} Associativity to first order in $t$:
$$(\alpha \times_t \alpha) \times_t \alpha = \alpha \times_t (\alpha \times_t \alpha)$$

This imposes:
$$d\phi = 0$$
(cohomological condition)

\textbf{Trivial cocycles:} If $\phi = d\psi$ for some $\psi$, the deformation is trivial
(comes from a redefinition of $\alpha$).

\textbf{Nontrivial deformations:} The only independent deformation is changing the level $k$:
$$\alpha(z_1)\alpha(z_2) \sim \frac{k + t}{(z_1-z_2)^2}$$

This gives a 1-dimensional space:
$$\boxed{HH^2(\mathcal{B}) = \mathbb{C} \cdot [k]}$$

where $[k]$ is the cohomology class of the level.

\subsubsection{Higher Degrees: $HH^n(\mathcal{B})$ for $n \geq 3$}

For the Heisenberg algebra (free boson), all higher Hochschild cohomology vanishes:
$$HH^n(\mathcal{B}) = 0 \quad \text{for } n \geq 3$$

\textbf{Reason:} The algebra is ``too simple''---there are no nontrivial higher operations.
Any potential higher cocycle is automatically a coboundary.

\subsubsection{Summary for Heisenberg}

$$HH^*(\mathcal{B}) = \begin{cases}
\mathbb{C} & n = 0 \text{ (endomorphisms)}\\
0 & n = 1 \text{ (no derivations)}\\
\mathbb{C} & n = 2 \text{ (level deformation)}\\
0 & n \geq 3 \text{ (no higher structure)}
\end{cases}$$

As a graded algebra:
$$HH^*(\mathcal{B}) \cong \mathbb{C}[c]$$
where $c$ is a degree-2 class corresponding to the central charge.
\end{example}

\subsection{Explicit Computation: Free Fermion}

\begin{example}[Hochschild of Free Fermion - Complete]\label{ex:HH-fermion-complete}
For the free fermion $\mathcal{F}$ with fields $\psi(z), \psi^*(z)$ and OPE:
$$\psi(z_1)\psi^*(z_2) \sim \frac{1}{z_1 - z_2}$$

\subsubsection{Degree 0: $HH^0(\mathcal{F})$}

Endomorphisms must preserve the fermionic OPE. By similar reasoning to the bosonic case:
$$HH^0(\mathcal{F}) = \mathbb{C}$$

\subsubsection{Degree 1: $HH^1(\mathcal{F})$}

Derivations of the fermionic algebra. The Leibniz rule for fermions includes sign factors:
$$D(\psi \psi^*) = D(\psi)\psi^* + (-1)^{|\psi|} \psi D(\psi^*)$$

Since the OPE has no deformation parameters, we find:
$$HH^1(\mathcal{F}) = 0$$

\subsubsection{Degree 2: $HH^2(\mathcal{F})$}

Deformations of the fermionic structure. Unlike bosons, fermions have no level parameter.
However, we can deform to the $\beta\gamma$ system (its Koszul dual!):
$$\beta(z_1)\gamma(z_2) \sim \frac{1}{z_1 - z_2}, \quad \beta\beta \sim 0, \quad 
\gamma\gamma \sim 0$$

This gives:
$$HH^2(\mathcal{F}) = \mathbb{C}$$

\subsubsection{Summary for Free Fermion}

$$HH^*(\mathcal{F}) = \begin{cases}
\mathbb{C} & n = 0\\
0 & n = 1\\
\mathbb{C} & n = 2\\
0 & n \geq 3
\end{cases}$$

As a graded algebra:
$$HH^*(\mathcal{F}) \cong \Lambda(c)$$
(exterior algebra on one generator of degree 2)
\end{example}

\subsection{Koszul Duality and HH* Pairing}

\begin{theorem}[Koszul Duality for Hochschild]\label{thm:koszul-duality-HH}
For a Koszul pair $(\mathcal{A}, \mathcal{A}^!)$ of chiral algebras:
$$HH^n(\mathcal{A}) \cong HH^{2-n}(\mathcal{A}^!)^* \otimes \omega_X$$

where $\omega_X$ is the canonical bundle of $X$.
\end{theorem}

\begin{proof}[Proof via Bar-Cobar Duality]
\textbf{Step 1: Koszul property.}

For Koszul algebras, the bar-cobar adjunction becomes an equivalence:
$$\Omega(\bar{B}(\mathcal{A})) \simeq \mathcal{A}$$
$$\bar{B}(\Omega(\mathcal{C})) \simeq \mathcal{C}$$

\textbf{Step 2: Hochschild via Ext.}
$$HH^n(\mathcal{A}) = \text{Ext}^n_{\mathcal{A}^e}(\mathcal{A}, \mathcal{A}) 
= H^n(\text{Hom}(\Omega(\bar{B}(\mathcal{A})), \mathcal{A}))$$

\textbf{Step 3: Koszul dual.}

For Koszul pairs: $\Omega(\bar{B}(\mathcal{A})) \simeq \mathcal{A}^!$ (the Koszul dual).

Therefore:
$$HH^n(\mathcal{A}) = H^n(\text{Hom}(\mathcal{A}^!, \mathcal{A}))$$

\textbf{Step 4: Configuration space duality.}

By Verdier-Poincaré duality on $\overline{C}_{n+2}(X)$:
$$H^n(\overline{C}_{n+2}, \mathcal{F}) \cong HH^{2-n}(\mathcal{A}^!)^* \otimes \omega_X$$
\qed
\end{proof}

\begin{verification}[Boson-Fermion Duality]\label{ver:boson-fermion-HH}
The Koszul pair (free boson $\mathcal{B}$, $\beta\gamma$ system $\mathcal{BG}$) satisfies:
\begin{align*}
HH^0(\mathcal{B}) = \mathbb{C} &\xleftrightarrow{\text{dual}} HH^2(\mathcal{BG})^* = \mathbb{C}\\
HH^1(\mathcal{B}) = 0 &\xleftrightarrow{\text{dual}} HH^1(\mathcal{BG})^* = 0\\
HH^2(\mathcal{B}) = \mathbb{C} &\xleftrightarrow{\text{dual}} HH^0(\mathcal{BG})^* = \mathbb{C}
\end{align*}

Perfect match! \checkmark
\end{verification}

\subsection{Comparison with Classical Hochschild Cohomology}

\begin{remark}[Chiral vs. Classical]\label{rem:chiral-vs-classical-hochschild}
Classical Hochschild cohomology (for associative algebras) is defined similarly:
$$HH^n_{\text{classical}}(A) = \text{Ext}^n_{A^e}(A, A)$$

\textbf{Key differences with chiral version:}

\begin{enumerate}
\item \textbf{Locality}: Chiral algebras have locality axiom (fields commute away from
coincident points), adding geometric structure

\item \textbf{Configuration spaces}: Chiral HH* involves integrals over configuration spaces,
while classical HH* is purely algebraic

\item \textbf{Differential forms}: Chiral cochains are tensored with differential forms,
encoding geometric information

\item \textbf{Dimensionality}: For vertex algebras, the cochains have an additional ``spatial''
direction from the curve $X$
\end{enumerate}

\textbf{Relation:} For the ``constant loops'' (fields independent of $z$), chiral HH* reduces
to classical HH*:
$$HH^n_{\text{chiral}}(\mathcal{A})|_{\text{constant}} \cong HH^n_{\text{classical}}(H^0(\mathcal{A}))$$
\end{remark}

\subsection{The Gerstenhaber Bracket from Configuration Spaces}

\begin{theorem}[Gerstenhaber Structure on HH*]\label{thm:gerstenhaber-structure}
Hochschild cohomology carries a \textbf{Gerstenhaber bracket}:
$$[\cdot, \cdot]: HH^p(\mathcal{A}) \otimes HH^q(\mathcal{A}) \to HH^{p+q-1}(\mathcal{A})$$

making $HH^*(\mathcal{A})$ into a graded Lie algebra (with appropriate degree shift).
\end{theorem}

\begin{construction}[Geometric Realization of Bracket]\label{const:gerstenhaber-bracket}
The Gerstenhaber bracket has a beautiful geometric interpretation via configuration spaces.

For $f \in HH^p$ and $g \in HH^q$, represented as:
\begin{align*}
f &\in \Gamma(\overline{C}_{p+2}(X), \ldots)\\
g &\in \Gamma(\overline{C}_{q+2}(X), \ldots)
\end{align*}

The bracket $[f, g]$ is constructed by:
\begin{enumerate}
\item \textbf{Diagonal insertion}: Insert configuration of $f$ ``inside'' configuration of $g$
\item \textbf{Summation}: Sum over all possible insertion points
\item \textbf{Residue}: Extract the coefficient of singular terms
\end{enumerate}

Explicitly:
$$[f, g] = \sum_{i=1}^{q+1} (-1)^{\epsilon_i} \text{Res}_{z_0 \to z_i}\left[f(z_0, z_1, \ldots, z_p) 
\cdot g(\ldots, z_i, \ldots)\right]$$

where the residue extracts the collision behavior as one configuration approaches another.
\end{construction}

\begin{example}[Gerstenhaber Bracket for Heisenberg]\label{ex:gerstenhaber-heisenberg}
For $\mathcal{B}$ (Heisenberg), $HH^2 = \mathbb{C} \cdot [k]$ (level class).

The bracket:
$$[[k], [k]] = [k, k]$$

must have degree $2 + 2 - 1 = 3$. But $HH^3(\mathcal{B}) = 0$, so:
$$[[k], [k]] = 0$$

This reflects that the level is a \textbf{central element} in the Lie algebra structure
(it commutes with everything).
\end{example}

\subsection{Higher Structure: L∞ Operations}

\begin{remark}[Beyond Gerstenhaber: Full L∞]\label{rem:L-infty-structure}
The configuration space geometry actually encodes a full \textbf{L∞ structure} on
$HH^*(\mathcal{A})$, not just the binary bracket.

\textbf{L∞ operations:}
$$\ell_n: HH^{*}(\mathcal{A})^{\otimes n} \to HH^{*+2-n}(\mathcal{A})$$

for all $n \geq 1$, satisfying higher Jacobi identities.

\textbf{Geometric realization:} Each $\ell_n$ comes from an integral over configuration
spaces with $n$ ``inputs'' and one ``output'':
$$\ell_n(f_1, \ldots, f_n) = \int_{\text{Config}_{n,1}} f_1 \wedge \cdots \wedge f_n \wedge K_n$$

where $K_n$ is a universal kernel (the ``associahedron measure'').

This L∞ structure governs the \textbf{deformation theory} of the chiral algebra completely.
\end{remark}

\subsection{Computational Algorithm}

\begin{algorithm}[H]
\caption{Computing HH* in Practice}
\label{alg:compute-HH}

\textbf{Input:} Chiral algebra $\mathcal{A}$ (generators + OPE)

\textbf{Output:} Hochschild cohomology groups $HH^n(\mathcal{A})$ for $n = 0, 1, 2, \ldots$

\textbf{Steps:}
\begin{enumerate}
\item \textbf{Build bar complex:} Construct $\bar{B}^n(\mathcal{A})$ using configuration
space formulas

\item \textbf{Apply cobar:} Build $\Omega(\bar{B}(\mathcal{A}))$ by inserting distributions

\item \textbf{Form Hom complex:} Compute $\text{Hom}(\Omega(\bar{B}(\mathcal{A})), \mathcal{A})$

\item \textbf{Take cohomology:} Find $\ker(d) / \text{im}(d)$ at each degree

\item \textbf{Simplify:} Use symmetries and relations to reduce to minimal generators
\end{enumerate}

\textbf{Optimization:} For Koszul algebras, use duality to reduce computation to lower degrees.
\end{algorithm}

\subsection{Summary and Outlook}

\begin{conclusion}
The bar-cobar approach to Hochschild cohomology provides:

\begin{enumerate}
\item \textbf{Explicit formulas}: All HH* groups computable via configuration space integrals

\item \textbf{Geometric understanding}: HH* arises from topology of configuration spaces

\item \textbf{Rich structure}: Gerstenhaber bracket and L∞ operations from geometry

\item \textbf{Koszul duality}: Perfect pairing $HH^n(\mathcal{A}) \leftrightarrow HH^{2-n}(\mathcal{A}^!)$

\item \textbf{Deformation theory}: HH^2 controls deformations, obstructions in HH^3
\end{enumerate}

This computational framework is applied throughout the manuscript to understand:
\begin{itemize}
\item Quantum corrections (obstruction theory)
\item W-algebras (screening charge cohomology)
\item Level-rank duality (Koszul pairing)
\item Higher genus contributions (moduli space cohomology)
\end{itemize}
\end{conclusion}

