\chapter{BV-BRST formalism and Gaiotto's perspective}
\label{ch:v1-bv-brst}
\index{Batalin--Vilkovisky|see{BV algebra}}

The BRST complex and the chiral bar complex compute the same
derived quotient only on their common genus-$0$ surface. Costello's
BV formalism supplies the derived moduli problem of gauge fields;
the chiral bar construction supplies the collision coalgebra of the
boundary algebra. A comparison theorem must specify the surface on
which these two presentations meet.

On $X=\mathbb{P}^1$, after gauge fixing and on the uncurved relative
complex, the classical BV equation is transported to the square-zero
bar equation. The quantum master equation uses the convention
\[
\hbar \Delta_{\mathrm{BV}}S+\tfrac{1}{2}\{S,S\}_{\mathrm{BV}}=0,
\]
with the factor $\tfrac{1}{2}$ fixed as in
Appendix~\ref{app:signs}. Its genus-$0$ classical part
corresponds to $d_{\mathrm{bar}}^2=0$ under the comparison; the
Laplacian and higher-genus sewing terms require additional data.
For the bosonic string, $c_{\mathrm{matter}}=26$ is the BRST
nilpotence condition for matter plus the $bc$ ghost system, equivalently
the vanishing of the BRST conductor
$K_{\mathrm{BRST,tot}}=(c_{\mathrm{matter}}-26)/2$. This conductor is
the Virasoro half-central-charge seen by the reparametrisation ghosts;
it is not the trace-form collision characteristic
$\kappa(\mathcal H^{\oplus 26}_1)=26$. The Virasoro Koszul self-dual
point is $c = 13$, a different condition.

A natural obstruction sits in the way. At higher genus, the BV
Laplacian receives contributions from handle-gluing amplitudes that
involve the full moduli space $\overline{\mathcal{M}}_{g,n}$, while
the bar differential collects OPE residues along FM boundary strata.
What is proved in this chapter is the genus-$0$ BV/bar comparison
and the all-genera scalar Heisenberg identity, together with the
all-genera coderived comparison of
Theorem~\ref{thm:bv-bar-coderived-vol1}. Beyond genus~$0$, the
obstruction analysis isolates why classes~$\mathsf{G}$,
$\mathsf{L}$, and~$\mathsf{C}$ admit stronger chain-level statements
than class~$\mathsf{M}$. The higher-genus comparison is resolved in
$D^{\mathrm{co}}$ because the harmonic discrepancy factors through
the curvature and the resulting cone is $m_0$-torsion, hence
coacyclic. The stronger chain-level statement is unconditional for
classes~$\mathsf{G}$ and~$\mathsf{L}$, conditional for
class~$\mathsf{C}$ on harmonic decoupling, and fails for
class~$\mathsf{M}$. The Heisenberg case is resolved at the
scalar level at all genera:
$F_g^{\mathrm{BV}}(\cH_\kappa) = F_g^{\mathrm{bar}}(\cH_\kappa)
= \kappa \cdot \lambda_g^{\mathrm{FP}}$
\textup{(}Theorem~\ref{thm:heisenberg-bv-bar-all-genera-vol1}\textup{)}.
For general algebras what survives at every genus is the scalar
anomaly package: the universal MC class $\Theta_\cA$ encodes the
one-loop anomaly coefficient $\kappa(\cA)$, and its projection
onto $H^2(\overline{\mathcal{M}}_{g,n})$ gives $F_g = \kappa(\cA) \cdot \lambda_g$
on the uniform-weight lane \textup{(}Theorem~D\textup{)}. The
multi-weight correction $\delta F_g^{\mathrm{cross}}$ is where the
chain-level identification breaks: the cross-channel term in the
sewing expansion has no counterpart in the BV side until
harmonic decoupling is assumed, and class~$\mathsf{M}$ is precisely
where that assumption fails.

\begin{remark}[BRST anomaly brackets and transferred SC operations]
\label{rem:brst-anomaly-gkw}
\index{Gaiotto--Kulp--Wu!BRST anomaly brackets}
\index{BRST operator!GKW higher operations}
The BRST-anomaly brackets of Gaiotto--Kulp--Wu~\cite{GKW2025}
and the transferred $\mathrm{SC}^{\mathrm{ch,top}}$ operations of
the bar complex describe the same deformation problem on the
genus-$0$ overlap: GKW compute higher operations from Wess--Zumino
consistency on a disk chart; the bar complex computes them from
iterated residues on FM boundary strata
(Remark~\ref{rem:iterated-residues-ainfty}).
The MC equation $D \cdot \Theta + \tfrac{1}{2}[\Theta, \Theta] = 0$
(Theorem~\ref{thm:mc2-bar-intrinsic}) is the all-genera master
equation of which GKW's consistency conditions are the genus-$0$
projections.
\end{remark}

\begin{remark}[Universal-conductor identity: BV/BRST instance;
\ClaimStatusConditional]
\label{rem:bv-brst-universal-conductor}
\index{universal conductor!BV/BRST instance|textbf}
\index{ghost charge!conductor formula}
\index{KSDual!ghost-trace alignment}
\emph{Type signature.} (Open quadrant; chain-level presentation;
Beilinson level $4$ on the chosen ghost resolution; hypothesis
package: conformal chiral algebra $\cA$ with chosen stress tensor and
chosen BRST ghost system; KSDual scope for the equality with the
trace-form conductor.)

For a conformal chiral algebra with chosen stress tensor set
\[
 K_{\mathrm{BRST}}(\cA):=\frac{1}{2}c(\cA).
\]
This is the Virasoro conductor measured by the BRST ghost current. It
agrees with the modular characteristic only in lineages where the
standard-landscape ratio gives $\kappa=c/2$; it differs from the
Heisenberg collision invariant, where
$\kappa(\mathcal H^{\oplus d}_1)=d$ while
$K_{\mathrm{BRST}}(\mathcal H^{\oplus d}_1)=d/2$. The
matter-plus-ghost cancellation
$K_{\mathrm{BRST,tot}}=0\Leftrightarrow Q_{\mathrm{BRST}}^2=0$
(Lemma~\ref{lem:brst-nilpotence}, Remark~\ref{rem:brst-nilpotence-periodicity})
is the BV/BRST instance of the ghost-resolution conductor identity
\[
 K_{\mathrm{univ}}^{\mathrm{BRST}}(\cA)
 \;=\; -\,\frac{1}{2}\,
 c_{\mathrm{ghost}}\bigl(\BRST(\cA)\bigr).
\]
The conductor $K_{\mathrm{univ}}^{\mathrm{BRST}}$ is attached to a
chosen BRST ghost resolution. It is not the ordered-collision invariant
$\kappa(\cA)$, and it is not the Theorem~C complementarity conductor
$K^\kappa(\cA,\cA^!)=\kappa(\cA)+\kappa(\cA^!)$ without an additional
comparison theorem. The ghost-trace conductor is scope-aligned to the
$\mathbb{Z}/2$-fixed sublocus $\mathrm{KSDual}\subset\mathrm{Kosz}(X)$
under the chiral/antichiral involution $\cA\mapsto\cA^!$: on KSDual
the half-normalisation $K_{\mathrm{BRST}}=\tfrac12 c$ pairs with the
Theorem~C complementarity conductor as the equivariant signature, and
the ghost-trace pairs with the bulk
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ under the
ghost-resolution-to-derived-centre comparison morphism. Off KSDual the
conductor is a chosen-resolution invariant only. Chapter~\ref{chap:universal-conductor} records the
full central-charge normalisation; the present BRST comparison uses the
half-normalisation matching the Virasoro convention
$\kappa(\mathrm{Vir}_c)=c/2$. The identity records the conformal anomaly
cost that a BRST gauging must absorb.
For the bosonic string the reparametrisation ghost system has
$c_{bc}=-26$ and $K_{\mathrm{BRST}}(bc)=-13$; the free matter sector
has $c_{\mathrm{matter}}=26$ and
$K_{\mathrm{BRST}}(\mathcal H^{\oplus 26}_1)=13$, so the total BRST
conductor vanishes. The separate collision invariant remains
$\kappa(\mathcal H^{\oplus 26}_1)=26$.

For the WZW example $\cA=V_k(\fg)$ the affine ghost system contributes
$c_{\mathrm{ghost}}^{\mathrm{WZW}}=-2\dim(\fg)$
(Remark~\ref{rem:wzw-brst-bar-generic-level}), hence
$-\tfrac12c_{\mathrm{ghost}}^{\mathrm{WZW}}=\dim(\fg)$. This cancels
the Virasoro conductor of the Feigin--Frenkel pair:
\[
 \frac{1}{2}\Bigl(c(V_k(\fg))+c(V_{-k-2h^\vee}(\fg))\Bigr)
 = \dim(\fg)
 = -\tfrac{1}{2}\,c_{\mathrm{ghost}}^{\mathrm{WZW}}.
\]
The trace-form modular characteristic obeys the different identity
\[
 \kappa(V_k(\fg))+\kappa(V_{-k-2h^\vee}(\fg))=0,\qquad
 \kappa(V_k(\fg))=\frac{\dim(\fg)(k+h^\vee)}{2h^\vee},
\]
as recorded in the landscape census. Thus the ghost conductor cancels
central charge, while Verdier complementarity cancels the trace-form
curvature coefficient.
Chapter~\ref{chap:universal-conductor} is the reference for the
ghost-resolution conductor and for any theorem comparing it with the
central-charge, Euler, or ghost-number carriers under their stated
hypotheses. The cross-volume bridge identifies the genus-$0$ shadow of
the boundary-bulk ghost-cancellation formula obtained from Vol~II's
universal holographic master theorem
(Vol~II Theorem~\ref{V2-thm:universal-holography-master}, cited
across the volume boundary; cf.\ also the climax identity
$d_{\mathrm{bar}} = \mathrm{KZ}^*(\nabla_{\mathrm{Arnold}})$ of
Chapter~\ref{ch:climax-theorem}).
\end{remark}

\begin{remark}[Structural cross-references]
\label{rem:bv-brst-anchors}
\index{BV/BRST!structural cross-references}
The BV/BRST chapter sits at three structural anchor
points:
\begin{enumerate}[label=\textup{(W\arabic*)}]
\item \emph{Universal conductor.} The identity
 $K_{\mathrm{univ}}^{\mathrm{BRST}}(\cA)
 =-\tfrac12c_{\mathrm{ghost}}(\BRST(\cA))$ is the ghost-resolution
 conductor functor of Chapter~\ref{chap:universal-conductor};
 Lemma~\ref{lem:brst-nilpotence} is its genus-$0$ instance. Identifying
 this carrier with the ordered-collision invariant $\kappa(\cA)$ is a
 separate comparison statement and is not automatic.
\item \emph{Bar--cobar reconstruction.} The bar/cobar counit
 $\Omega(\barB(\cA)) \to \cA$ belongs to reconstruction, not to
 BRST and not to Verdier/Koszul duality. Theorem~\ref{thm:bv-bar-geometric}
 supplies a genus-$0$ comparison between the gauge-fixed BV complex
 and the geometric bar complex; Theorem~A supplies the separate
 reconstruction map from the bar coalgebra back to~$\cA$ on the
 Koszul locus.
\item \emph{Climax identity.} The genus-$0$ BV/bar identification
 transports $Q_{\mathrm{BRST}}$ to $d_{\mathrm{bar}}$ on the
 relative nilpotent locus $c_{\mathrm{matter}}=26$. This is one
 face of the climax identity $d_{\mathrm{bar}} =
 \mathrm{KZ}^*(\nabla_{\mathrm{Arnold}})$,
 together with the corresponding BRST ghost-conductor comparison in
 Chapter~\ref{ch:climax-theorem}: the bar differential and the
 Arnold connection are pulled back to the same operator on the
 BRST-cohomologically nilpotent locus.
\end{enumerate}
The cross-volume bridge to Vol~III is via the two-stage
CY-to-chiral functor
$\Phi_d^{(\Sigma_{d-1}, C)}
=\mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}\circ\Phi_d^{\mathrm{FA}}$
at $d=3$, with specialisation data $(\Sigma_{d-1}, C)$ named
explicitly: on the five verified Borcherds families
$N \in \{1,2,3,4,6\}$, the conjectural comparison is between the
present BV/BRST conductor and the proved Borcherds weight
$\kappa_{\BKM}(X)=c_N(0)/2$ in the BPS-counting category. The
level-$0$ vertical companion is the factorisation dg-cat on
$(X, D, \tau)$ identified with Vol~III's CY-cat via 6d holomorphic
Chern--Simons under a \emph{quartic} anomaly polynomial
$\int_X\Tr_{\mathrm{ad}}\bigl(A(F_A)^3\bigr)$ on the CY$_3$ trivialised
by $\omega_X\cong\mathcal{O}_X$. The dimensional shift to
six dimensions raises the obstruction to degree~$4$ in the gauge field
$A$, distinguishing it from the cubic-Casimir anomaly of $5$d hCS; the
identification ``$6$d hCS $=$ $3$d CS in disguise'' has no type.
Companion remark: \ref{rem:bvbrst-6d-hcs-quartic}.
\end{remark}

\begin{remark}[BV/bar dictionary; \ClaimStatusHeuristic]
\label{rem:bv-bar-bridge}
\index{BV algebra!bar complex bridge|textbf}
\emph{Type signature.} (Open quadrant; chain-level on item~(i),
$(\infty, 1)$-categorical heuristic on items~(ii)--(iii); Beilinson
levels $1$--$2$ on the gauge-fixed BV/bar identification, level $4$
on the modular characteristic; hypothesis package: chiral algebra
$\cA$ on a smooth curve $X$ with chosen stress tensor and chosen
gauge fixing $\mathcal L$.)

Let $\cA$ be a chiral algebra on a smooth curve~$X$. The BV and
bar-cobar formalisms are related by the following dictionary:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the geometric BV complex and the geometric bar complex are
 identified at genus~$0$
 \textup{(}Theorem~\textup{\ref{thm:bv-bar-geometric}}, proved
 elsewhere\textup{)};
\item the classical master equation corresponds to the
 genus-$0$ square-zero condition for the bar differential after
 transporting through that external comparison;
\item the scalar genus-$1$ obstruction is the modular characteristic
 $\kappa(\cA)$, the one-loop anomaly
 coefficient.
\end{enumerate}
The chain-level identifications (antifields versus
cogenerators, the BV Laplacian, the full quantum master equation,
BRST versus bar cohomology) remain heuristic in this manuscript.

Item~\textup{(i)} is Theorem~\ref{thm:bv-bar-geometric}. The scalar
genus-$1$ coefficient in item~\textup{(iii)} is the content of
Theorem~\ref{thm:genus-universality} and, for Virasoro, of
Computation~\ref{comp:virasoro-curvature}. The remaining entries are
the intended BV reading of these proved algebraic statements, not
chain-level equalities.
\end{remark}

\begin{remark}[Heuristic BV reading of the modular MC hierarchy]
\label{rem:modular-qme-bv}
\index{quantum master equation!modular}
\index{modular quantum master equation|textbf}

The proved object is the universal Maurer--Cartan class~$\Theta_\cA$
\textup{(}Theorem~\ref{thm:mc2-bar-intrinsic}\textup{)}.
Write $\Theta_\cA = \Theta_0 + \hbar\,\Theta_1 + \hbar^2\,\Theta_2
+ \cdots$ for the genus expansion. The BV-shaped modular equation
\begin{equation}\label{eq:modular-qme-bv}
d\,\Theta_\cA + \tfrac{1}{2}[\Theta_\cA, \Theta_\cA]
+ \hbar\,\Delta\,\Theta_\cA = 0
\end{equation}
in the completed cyclic deformation Lie algebra
$\Defcyc^{\mathrm{mod}}(\cA)$ breaks into a hierarchy:
\begin{alignat*}{2}
&\text{genus } 0\colon\quad
 &&d\,\Theta_0 + \tfrac{1}{2}[\Theta_0,\Theta_0] = 0
 \qquad\text{(classical ME $=$ $d_{\mathrm{bar}}^2 = 0$)}, \\
&\text{genus } 1\colon\quad
 &&d\,\Theta_1 + [\Theta_0,\Theta_1] + \Delta\,\Theta_0 = 0
 \qquad\text{(one-loop anomaly $=$ $\kappa(\cA)\cdot\omega_1$)}, \\
&\text{genus } 2\colon\quad
 &&d\,\Theta_2 + [\Theta_0,\Theta_2]
 + \tfrac{1}{2}[\Theta_1,\Theta_1]
 + \Delta\,\Theta_1 = 0
 \qquad\text{(two-loop interference)}.
\end{alignat*}
The displayed hierarchy is a heuristic BV translation of the proved
modular MC hierarchy, not a proved BV identity: the
genus-$0$ line is a classical master equation, the genus-$1$
line a one-loop anomaly equation, and higher lines encode
nonlinear modular interference. At the scalar level, the trace
of~\eqref{eq:modular-qme-bv} recovers the genus tower
$F_g = \kappa(\cA)\lambda_g$ on the uniform-weight lane by
Theorem~D. At the
full level, no BV identity is asserted here; equation~\eqref{eq:modular-qme-bv}
is the conjectural target of the modular cumulant transform
(\S\ref{subsec:completion-kinematics-theory} of the concordance).

In the Feynman-diagram language of
Chapter~\ref{ch:v1-feynman}: $\Theta_0$ collects tree
diagrams, $\Theta_1$ collects one-loop diagrams, and $\Theta_g$
collects connected $g$-loop diagrams. In physics language, the modular MC hierarchy is an all-loop Ward identity. The connected
stable-graph exponential
$\Theta_\cA = \sum_{\Gamma\,\text{connected}}
\frac{\hbar^{g(\Gamma)}}{|\operatorname{Aut}(\Gamma)|}\,\Phi_\Gamma$
makes this precise: the vertices are cumulant primitives, internal
edges are factorization propagators, and the symmetry factor is the
standard graph automorphism weight.
\end{remark}

\begin{remark}[String field theory interpretation; \ClaimStatusHeuristic]
\label{rem:sft-bar-identification}
\index{string field theory!bar complex identification}
\index{bar complex!string field theory reading}
In the heuristic string-field-theory reading, the genus-$0$
bar--BRST comparison sends the bar differential
$d_{\barB}$ to the BRST charge~$Q$ of open string field theory. The
bar curvature~$m_0$ then plays the role of the tadpole, the shadow
amplitude $\mathrm{Sh}_{g,n}(\Theta_\cA)$ plays the role of the
closed SFT vertex at genus~$g$ with $n$~punctures, and the MC
equation is the algebraic analogue of the classical closed SFT
master equation.
\end{remark}

\section{BV formalism for chiral algebras}

\begin{definition}[BV data for a chiral algebra]
\label{def:bv-data-chiral}
\index{antibracket}
\index{BV algebra!data}
Let $\cA$ be a chiral algebra on a smooth curve~$X$.
The BV formalism associates to~$\cA$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Fields}: $\phi \in \mathcal{A}$, sections of the chiral algebra sheaf.
\item \emph{Antifields}: $\phi^+ \in \mathcal{A}^*[1]$, the Serre dual shifted by~$1$.
\item \emph{BV bracket}: the degree-$+1$ odd Poisson bracket
 $\{-,-\}_{\mathrm{BV}}$ generated by the shifted Serre pairing,
 with graded skew sign
 $\{F,G\}_{\mathrm{BV}}
 = -(-1)^{(|F|+1)(|G|+1)}\{G,F\}_{\mathrm{BV}}$.
\item \emph{Action}: $S[\phi, \phi^+]$ satisfying the classical master
 equation $\{S,S\}_{\mathrm{BV}} = 0$.
\end{enumerate}
\end{definition}

\begin{theorem}[Genus-$0$ BV complex and geometric bar complex;
\ClaimStatusProvedElsewhere{} \cite{CG17}]
\label{thm:bv-bar-geometric}
\index{BV algebra!bar complex identification}
\emph{Type signature.} (Open quadrant; chain-level presentation;
Beilinson levels $1\to 2$, the bar-coalgebra direction; hypothesis
package: chiral algebra on $X=\mathbb{P}^1$, BV presentation with
local observables recovering $\cA$, genus-$0$ uncurved surface.)

Let $\cA$ be a chiral algebra on $X = \mathbb{P}^1$, equipped with a
BV presentation whose local observables recover~$\cA$. On the
genus-$0$ uncurved surface there is a quasi-isomorphism
\[
C_{\mathrm{BV}}(\mathcal{A}) \xrightarrow{\;\sim\;}
\barB^{\mathrm{ch}}(\mathcal{A}).
\]
Under this comparison, the classical BV differential
$Q_{\mathrm{BV}}=\{S,-\}_{\mathrm{BV}}$ is transported to the
genus-$0$ bar differential $d_{\mathrm{bar}}$. The comparison is the
Costello--Gwilliam BV/factorization-observable formalism specialized
to the chiral bar model; it is not a statement about the full QME or
about bar-cobar reconstruction.
\end{theorem}

\begin{proof}[Geometric construction supporting \textup{Theorem~\ref{thm:bv-bar-geometric}}]
\emph{Step~1: Bar generators.}

The degree-$n$ bar complex is:
\[\bar{B}^n(\mathcal{A}) = \Omega^*(\overline{C}_{n+1}(X), \mathcal{A}^{\boxtimes (n+1)})\]

The generators are operator insertions $\phi_i \in \mathcal{A}$ at marked points, paired with logarithmic $1$-forms $\eta_{ij} = d\log(z_i - z_j)$ dual to the collision divisors.

\emph{Step~2: BV bracket and signs.}

The BV bracket is a residue operation on the log-de~Rham complex
of~$\overline{C}_{n+1}(X)$, with the cohomological sign convention
of Appendix~\ref{app:signs}: for homogeneous functionals,
\[
\{F,G\}_{\mathrm{BV}}
=-(-1)^{(|F|+1)(|G|+1)}\{G,F\}_{\mathrm{BV}}.
\]
On desuspended bar generators the Koszul sign is the sign obtained by
moving $s^{-1}\phi$ past the intervening logarithmic form factors.
In local coordinates near the divisor
$D_{ij} = \{z_i = z_j\}$, with $\epsilon = z_i - z_j$, the
degree-zero residue component is:
\[\{\phi(z_i), \eta_{jk}\}
= \delta_{ij}\,\Res_{\epsilon = 0}
\Bigl[\frac{\partial\phi}{\partial z_i}\,
\frac{d\epsilon}{\epsilon(z_i - z_k)}\Bigr]
+ \delta_{ik}\,\Res_{\epsilon = 0}
\Bigl[\frac{\partial\phi}{\partial z_i}\,
\frac{d\epsilon}{\epsilon(z_i - z_j)}\Bigr].\]
Both terms are Poincar\'e residues of logarithmic forms along
normal-crossing divisors of the smooth
variety~$\overline{C}_{n+1}(X)$: the residue map
$\Res_{D_{ij}}\colon \Omega^k_{\log}(\overline{C}_{n+1})
\to \Omega^{k-1}_{D_{ij}}$ is an algebraic morphism of sheaves
on a smooth variety. The factor $1/(z_i - z_k)$ is a pole along
the transverse divisor $D_{ik}$ (Theorem~\ref{thm:FM}(3):
$D_{ij} \cap D_{ik}$ has normal crossings), so on~$D_{ij}$
it restricts to a regular meromorphic function with poles only
along~$D_{ij} \cap D_{ik}$, a codimension-$2$ stratum.
The FM compactification resolves all coincidence singularities
into normal-crossing divisors, and the log-de~Rham complex on
this resolution is the correct algebraic framework: it replaces
distributional regularization with algebraic residues.

The logarithmic $1$-forms $\eta_{ij} = d\log(z_i - z_j)$ generate
$H^1(C_n(X); \mathbb{C})$ by the Arnold--Brieskorn theorem;
for $X = \mathbb{C}$, all $\binom{n}{2}$ classes are linearly independent in degree~$1$
(the Arnold relations constrain products in degree~$\geq 2$), giving
$\dim H^1(C_n(\mathbb{C})) = \binom{n}{2}$. (For a curve of genus~$g > 0$, additional generators from $H^1(X)$ contribute $2gn$ classes.)

\emph{Step~3: Master equation.}

The classical master equation $\{S,S\}_{\mathrm{BV}}=0$ is transported
to $\dzero^2=0$ for the genus-$0$ bar differential:
\[d = d_{\text{strat}} + d_{\text{int}} + d_{\text{res}}\]
\end{proof}

\begin{remark}[Literature confirmation: Costello--Gwilliam]
The genus-$0$ BV/bar identification used in this chapter is consistent
with the Costello--Gwilliam BV formalism. In the CG framework, a
perturbative quantum field theory determines a factorization algebra of
observables, and for holomorphic theories this is the source of the
vertex-algebra structure treated in Chapter~5 of~\cite{CG17}.
Theorem~\ref{thm:bv-bar-geometric} is the chiral-bar model of that same
local observable package on $X=\mathbb{P}^1$: the BV differential is
the genus-$0$ bar differential, and collision residues are the
factorization products written in logarithmic-form language.

The overlap with~\cite{CG17} is the genus-$0$ local comparison and the
general BV/factorization dictionary. The bar-side genus expansion,
harmonic comparison, and coderived package are separate inputs; the
all-genera coderived theorem
\textup{(}Theorem~\ref{thm:bv-bar-coderived-vol1}\textup{)} belongs to
this chapter's construction, not to the theorem package attributed to CG.
\end{remark}

\subsection{Quantum master equation}

\begin{definition}[BV Laplacian]
\label{def:bv-laplacian}
\index{BV Laplacian|textbf}
The BV Laplacian $\Delta_{\mathrm{BV}}$ is the second-order differential operator
\[
\Delta_{\mathrm{BV}} = \sum_i \frac{\partial^2}{\partial \phi_i \partial \phi_i^+},
\]
contracting each field-antifield pair $(\phi_i, \phi_i^+)$.
In the geometric realization on $\barB^{\mathrm{ch}}(\cA)$, the heuristic formula
\[
\Delta_{\mathrm{BV}} \approx \sum_{i<j} \int \delta(z_i - z_j)\,
\frac{\partial}{\partial \eta_{ij}}
\]
inserts a diagonal residue, contracting the logarithmic form $\eta_{ij}$ via a
delta-function along $D_{ij}$. This is the loop-insertion operator in the bar
complex, distinct from the cobar functor $\Omega$ (which recovers $\cA$ from
$B(\cA)$ by bar-cobar inversion, Theorem~\ref{thm:bar-cobar-isomorphism-main}).
The precise algebraic version of this operator is conditional
\textup{(}Theorem~\ref{thm:config-space-bv}\textup{)}.
\end{definition}

\begin{remark}[Heuristic QME/MC comparison; \ClaimStatusHeuristic]
\label{rem:qme-bar-cobar}
\index{quantum master equation|textbf}
At genus~$0$, the classical part of the BV master equation matches the
square-zero bar differential after transporting through the external
comparison of Theorem~\ref{thm:bv-bar-geometric}. Extending this to a
full identification of the quantum master equation
\[
\hbar\,\Delta_{\mathrm{BV}}S + \tfrac{1}{2}\{S,S\}=0
\]
with a Maurer--Cartan equation in a BV-enhanced bar deformation
complex would require the conditional BV package recorded in
Theorems~\ref{thm:config-space-bv} and~\ref{thm:bv-functor}. That
full comparison is not proved here.

The classical genus-$0$ comparison combines the external BV/bar
identification with the square-zero bar differential on the
uncurved locus. The quantum, Laplacian, and functorial parts are
isolated as conditional content later in this chapter.
\end{remark}

\label{subsec:bv-bar-identification}
\index{BV algebra!bar complex identification}

\begin{remark}[Heuristic genus-\texorpdfstring{$0$}{0} amplitude/bar comparison;
\ClaimStatusHeuristic]\label{rem:genus0-amplitude-bar}
\index{string amplitude!bar complex}
Let $\cA$ be a chiral algebra on $\mathbb{P}^1$, and let
$\omega_1, \ldots, \omega_n$ be cocycles in
$\bar{B}^1(\cA)$. The heuristic genus-$0$ string-amplitude pairing
\[
\mathcal{A}_0(\omega_1, \ldots, \omega_n)
\;=\;
\int_{\overline{\mathcal{M}}_{0,n}}
 \omega_1 \wedge \cdots \wedge \omega_n
\]
parallels the bar-complex Euler characteristic
$\chi(\bar{B}^n_0(\cA))$, where $\bar{B}^n_0$ denotes the
genus-$0$ component of the degree-$n$ bar complex. The exact
identification between these two quantities is not proved in the
manuscript.
The bar complex is realized on
$\overline{C}_n(\mathbb{P}^1) = \overline{\mathcal{M}}_{0,n+1}$
(Theorem~\ref{thm:bar-cobar-isomorphism-main}),
with the bar differential given by residues of the FM propagator
$\eta_{ij} = d\log(z_i - z_j)$ along collision divisors.
The displayed comparison is the expected physics reading of these
configuration-space forms, but the chapter does not prove the required
identification between the physical integration pairing and the Euler
characteristic of the genus-$0$ bar complex.
\end{remark}

\begin{remark}[Genus-$1$ partition function]\label{rem:genus1-bv}
At genus~$1$, the $\hat{A}$-genus gives $F_1 = \kappa(\cA)/24$
\textup{(}Theorem~D\textup{)}. For $\cA = \mathrm{Vir}_c$ with
$\kappa(\mathrm{Vir}_c) = c/2$: $F_1 = c/48$.
\end{remark}

\begin{remark}[Anomaly as curvature]\label{rem:anomaly-curvature-bv}
\index{anomaly!curvature identification}
By Theorem~\ref{thm:anomaly-koszul}, the genus-$0$ uncurved bar
model of
$\cA_{\mathrm{tot}}=\cA_{\mathrm{matter}}\otimes\cA_{\mathrm{ghost}}$
is square-zero on the BRST Virasoro lane if and only if
$K_{\mathrm{BRST,tot}}=0$; for the bosonic string this is the
condition $c_{\mathrm{matter}}=26$ after adding the $bc$ ghost system
of central charge $-26$. Outside this Virasoro lane the curvature
coefficient is the lineage-specific $\kappa(\cA)$ of the landscape
census. When that curvature coefficient is nonzero, the scalar
projection of the universal MC class is
$\Theta_\cA^{\min}=\kappa(\cA)\cdot\eta\otimes\Lambda$
\textup{(}Theorem~\ref{thm:explicit-theta}\textup{)}, and the
higher-genus fiberwise bar model is curved by this class.
\end{remark}

\section{Gauge fixing and BRST}

\subsection{BRST from BV}

\begin{definition}[BRST operator]
\label{def:brst-operator}
\index{BRST cohomology|textbf}
\index{BRST operator|textbf}
The BRST operator $Q_{\mathrm{BRST}}$ arises from gauge fixing the BV action.
Choose a Lagrangian submanifold $\mathcal{L}$ of the total space of fields and
antifields:
\[
Q_{\mathrm{BRST}} = Q_{\mathrm{BV}}\big|_{\mathcal{L}}.
\]
In the chiral algebra context, the BRST charge decomposes by antighost number
(not ghost number):
\[
Q_{\mathrm{BRST}} = Q_0 + Q_1 + Q_2 + \cdots,
\]
where $Q_k$ has antighost number~$k$ and operator dimension~$k-1$.
The total BRST charge has definite ghost number~$+1$.
\end{definition}

\begin{theorem}[BRST cohomology on a nilpotent gauge-fixed complex;
\ClaimStatusProvedElsewhere{} \cite{CG17,Polchinski1998}]
\label{thm:brst-physical-states}
Let a BV theory be equipped with a gauge-fixing Lagrangian
$\mathcal L$ such that the restricted BRST operator
$Q_{\mathrm{BRST}}$ is square-zero on the relative state complex and
all residual gauge symmetries are generated by this operator. Then
the physical on-shell state space is the BRST cohomology
\[
H^*(Q_{\mathrm{BRST}})\cong \mathcal A_{\mathrm{phys}}.
\]
\end{theorem}

\begin{example}[Free \texorpdfstring{$bc$}{bc} ghost system]
The $bc$ system has fields $b(z)$ of weight $\lambda$ and $c(z)$ of weight $1-\lambda$, OPE $b(z)c(w) \sim (z-w)^{-1}$, central charge $c_{bc} = 1 - 3(2\lambda - 1)^2$, and BRST operator $Q = \oint c(z) \bigl(T_{\text{matter}}(z) + \tfrac{1}{2}T_{\text{ghost}}(z)\bigr) dz$.

For the bosonic string, $\lambda = 2$ (so $b$ has weight~$2$ and $c$ has weight~$-1$), giving $c_{\text{ghost}} = 1 - 3(3)^2 = -26$ and ghost stress tensor $T_{\text{ghost}} = -2b\,\partial c - (\partial b)\,c$.

On the relative complex $\ker(b_0) \cap \ker(L_0^{\mathrm{tot}})$,
with the standard intercept normalisation, the BRST nilpotence
condition is:
\[
Q_{\mathrm{BRST}}^2 = 0
\iff c_{\mathrm{matter}} + c_{\mathrm{ghost}} = 0,
\quad\text{i.e., } c_{\mathrm{matter}} = 26
\]
(on the full complex, the anomaly is the quadratic ghost operator
of Lemma~\ref{lem:brst-nilpotence}, not a $c_0$ term).

In the bar complex, the residue component $d_{\mathrm{res}}$
of the bar differential heuristically corresponds to $Q_{\mathrm{BRST}}$
under the identification of Theorem~\ref{thm:bv-bar-geometric}.
\end{example}

\subsection{Coupling to topological gravity}

\begin{theorem}[Coordinate cocycle for collision logarithmic forms;
\ClaimStatusProvedHere]
\label{thm:log-form-ghost-law}
\index{ghost!transformation law}
\index{logarithmic form!ghost transformation}
The logarithmic forms $\eta_{ij} = d\log(z_i - z_j)$
on the configuration space $C_n(X)$ transform under a coordinate
change $z\mapsto w(z)$ by the exact logarithmic cocycle
\[
\eta_{ij} \;\mapsto\; \eta_{ij}
+ d\log\!\left(\frac{w(z_i) - w(z_j)}{z_i - z_j}\right).
\]
Near the diagonal $z_i \to z_j$, the correction term
approaches $d\log w'(z_i)$. Thus the FM propagator carries the
same coordinate-change cocycle that the Faddeev--Popov
diffeomorphism ghost detects after linearisation, but the
logarithmic form is an even de~Rham class, not the odd BRST ghost
field itself. The Arnold relations
$\eta_{ij} \wedge \eta_{jk} + \eta_{jk} \wedge \eta_{ki}
+ \eta_{ki} \wedge \eta_{ij} = 0$
in the Orlik--Solomon algebra provide the quadratic relation on
collision residues used by the genus-$0$ bar differential.
\end{theorem}

\begin{proof}
Direct computation: $\eta_{ij} = d\log(z_i - z_j)$
maps to $d\log(w(z_i) - w(z_j))$ under $z \to w(z)$.
Factoring:
\[
d\log(w(z_i) - w(z_j)) = d\log(z_i - z_j)
+ d\log\!\left(\frac{w(z_i) - w(z_j)}{z_i - z_j}\right)
\]
and near the diagonal, L'H\^opital gives
$(w(z_i) - w(z_j))/(z_i - z_j) \to w'(z_i)$, so
the correction approaches $d\log w'(z_i)$. Infinitesimally, for
$w(z)=z+\epsilon v(z)$,
\[
\delta_v\eta_{ij}
=d\!\left(\frac{v(z_i)-v(z_j)}{z_i-z_j}\right),
\]
whose diagonal limit is $d(v'(z_i))$. This is the coordinate
cocycle that enters the Faddeev--Popov ghost transformation, while
the parity and complex are different. The Arnold relations are
verified in Theorem~\ref{thm:arnold-relations}.
\end{proof}

\begin{conjecture}[Topological BRST comparison for collision ghosts;
\ClaimStatusConjectured]
\label{conj:v1-bar-topological-brst}
Let $\mathrm{Vect}(X)$ act on a chiral algebra~$\mathcal A$ by
conformal vector fields, and choose a Faddeev--Popov resolution of
this action. The coordinate cocycle of
Theorem~\ref{thm:log-form-ghost-law} is conjectured to extend to a filtered
genus-$0$ comparison map
\[
\Phi_{\mathrm{top}}\colon
C^*_{\mathrm{top}\text{-}\mathrm{BRST}}
(\mathcal A\otimes \mathrm{Vect}(X))
\longrightarrow
\bar{B}^{\mathrm{ch}}_0(\mathcal A),
\]
whose associated graded sends a ghost for the collision vector field
$z_i-z_j$ to the logarithmic form~$\eta_{ij}$. The conjectured
quasi-isomorphism is restricted to the nilpotent genus-$0$ relative
locus and requires the PBW lifting hypotheses of
Theorem~\ref{thm:brst-bar-genus0}; no all-genera dg-algebra
isomorphism is asserted.
\end{conjecture}

\section{The genus-\texorpdfstring{$0$}{0} BRST-bar chain map}
\label{sec:brst-bar-chain-map}
\index{BRST!bar complex chain map|textbf}

\subsection{Setup: the BRST complex}

Let $\cA$ be a conformal vertex algebra of central charge~$c$ on
$X = \mathbb{P}^1$, and let $\cA_{\mathrm{gh}} = bc$ denote the
$bc$-ghost system of weights $(2, -1)$ with $c_{\mathrm{gh}} = -26$.
The \emph{BRST complex} of~$\cA$ is the vertex algebra
$\cA_{\mathrm{tot}} = \cA \otimes \cA_{\mathrm{gh}}$ equipped with
the BRST differential:
\begin{equation}\label{eq:brst-differential}
Q_{\mathrm{BRST}}
= \oint \! c(z)\Bigl(T_{\cA}(z) + \tfrac{1}{2}\,T_{\mathrm{gh}}(z)\Bigr)\,dz
= \sum_{n \in \mathbb{Z}} \Bigl(
 \sum_m L^{\cA}_m\, c_{n-m}
 + \tfrac{1}{2}\sum_{p+q=n}(p-q)\, {:}b_p\, c_q\, c_{n-p-q}{:}
\Bigr)
\end{equation}
where $L^{\cA}_n$ are the Virasoro modes of~$\cA$ and $b_n, c_n$ are
the ghost modes with $\{b_m, c_n\} = \delta_{m+n,0}$. The
normal-ordering intercept is fixed to $a=1$; equivalently, in the
presentation
\[
Q_{\mathrm{BRST}}
=\sum_n c_{-n}(L_n^\cA+\tfrac12L_n^{\mathrm{gh}}-a\delta_{n,0})
\]
one takes
$a=1$. This is the convention used in
Lemma~\ref{lem:brst-nilpotence}.

\begin{lemma}[BRST nilpotence; \ClaimStatusProvedElsewhere{} \cite{FGZ86}]
\label{lem:brst-nilpotence}
Let $Q_{\mathrm{BRST}}$ be the bosonic-string BRST charge with
normal-ordering intercept $a=1$. As operators on the full
matter-plus-ghost Fock complex,
\[
 Q_{\mathrm{BRST}}^2
 =
 \frac{c_{\mathrm{matter}}-26}{12}
 \sum_{n\in\mathbb Z}(n^3-n)\,{:}c_{-n}c_n{:}.
\]
In particular, $Q_{\mathrm{BRST}}^2 = 0$ on the relative complex
$\cA_{\mathrm{tot}}^{\mathrm{rel}} = \ker(b_0) \cap \ker(L_0^{\mathrm{tot}})$
as an operator if and only if $c_{\mathrm{matter}}=26$.
\end{lemma}

\begin{remark}[BRST nilpotence and the bar construction]
\label{rem:brst-nilpotence-periodicity}
\index{nilpotence-periodicity correspondence!BRST instance}
The condition $Q_{\mathrm{BRST}}^2=0$ is the BRST instance of the
nilpotence-periodicity correspondence
(Remark~\ref{rem:nilpotence-periodicity}). The numerical invariant in
this sentence is the BRST conductor
\[
 K_{\mathrm{BRST,tot}}
 =\frac{c_{\mathrm{matter}}+c_{\mathrm{ghost}}}{2}
 =\frac{c-26}{2},
\]
not the bare trace-form characteristic of the underlying chiral
algebra. Vanishing of $K_{\mathrm{BRST,tot}}$ makes the relative
genus-$0$ bar model square-zero on the chosen stress-tensor lane. When
$K_{\mathrm{BRST,tot}}\neq0$, the quadratic ghost anomaly
$\frac{c_{\mathrm{matter}}-26}{12}
\sum_n(n^3-n){:}c_{-n}c_n{:}$ is the BRST curvature
obstructing nilpotence; the $n=0$ term vanishes because
$n^3-n=0$.
\end{remark}

For the bosonic string at $c_{\mathrm{matter}}=26$, the relative BRST
cohomology of $(\cA_{\mathrm{tot}},Q_{\mathrm{BRST}})$ is the
semi-infinite cohomology of the Virasoro action on the matter module,
graded by ghost number. This is the special Virasoro/string
realisation of the general semi-infinite construction defined in
\S\ref{sec:semi-infinite-bar}; it is not the definition of
semi-infinite cohomology for an arbitrary chiral algebra.

\subsection{The chain map}

\begin{theorem}[Genus-\texorpdfstring{$0$}{0} BRST-bar quasi-isomorphism;
\ClaimStatusConditional]
\label{thm:brst-bar-genus0}
\index{BRST!bar complex quasi-isomorphism}
Let $\cA$ be a PBW conformal vertex algebra on $\mathbb{P}^1$ with
$c(\cA) = 26$ \textup{(}so that
$\cA_{\mathrm{tot}} = \cA \otimes bc$ satisfies
$K_{\mathrm{BRST,tot}} = 0$\textup{)}. Assume the conformal-weight
filtrations on the relative BRST complex and on the genus-$0$ chiral
bar complex are complete and exhaustive, that their associated graded
complexes are identified by the classical bar--CE comparison, and that
the filtered lifting obstruction groups vanish. Then there exists a
chain map
\[
\Phi \colon
 \bigl(\cA_{\mathrm{tot}}^{\mathrm{rel}},\, Q_{\mathrm{BRST}}\bigr)
 \longrightarrow
 \bigl(\barB^{\mathrm{ch}}_0(\cA_{\mathrm{tot}}),\, d_{\mathrm{bar}}\bigr)
\]
from the relative BRST complex to the genus-$0$ bar complex, which is a
quasi-isomorphism of cochain complexes.
\end{theorem}

\begin{proof}
The hypotheses give a PBW filtration on both complexes, reducing the
comparison to the classical finite-dimensional setting at the
associated-graded level.

\emph{Step~1: Conformal weight filtration.}
Both complexes carry a $\mathbb{Z}_{\geq 0}$-filtration by
\emph{total conformal weight}:
\begin{align}
F^{\leq N}\cA_{\mathrm{tot}}^{\mathrm{rel}}
 &= \bigoplus_{\substack{\text{states of total}\\\text{weight } \leq N}}
 \cA_{\mathrm{tot}}^{\mathrm{rel}}, \\
F^{\leq N}\barB^{\mathrm{ch}}_0(\cA_{\mathrm{tot}})
 &= \bigoplus_{\substack{n \geq 0}}
 \Omega^{\leq N}\!\bigl(
 \overline{C}_{n+1}(\mathbb{P}^1),\,
 \cA_{\mathrm{tot}}^{\boxtimes(n+1)}
 \bigr),
\end{align}
where the filtration on bar generators counts the sum of conformal
weights of inserted operators plus the form degree on the
configuration space. Both differentials respect this filtration:
$Q_{\mathrm{BRST}}$ preserves conformal weight (the BRST current
has weight~$1$ and the contour integral lowers by~$1$), and the bar
differential $d_{\mathrm{bar}}$ is computed by OPE residues at
collision divisors, which preserve the total weight.

\emph{Step~2: Associated graded.}
On the associated graded $\mathrm{gr}\,F^{\bullet}$, both complexes
degenerate to classical constructions. For
$\mathrm{gr}\,\cA_{\mathrm{tot}}^{\mathrm{rel}}$: only the
weight-$0$ part of $Q_{\mathrm{BRST}}$ survives, which is the
Chevalley--Eilenberg differential of the finite-dimensional Lie algebra
$\mathfrak{g}_0 = \cA_{(1)}$ (the weight-$1$ subspace, viewed as a Lie
algebra via the zero-mode bracket $[a, b] = a_{(0)} b$).
For $\mathrm{gr}\,\barB^{\mathrm{ch}}_0(\cA_{\mathrm{tot}})$: only
the leading OPE pole contributes to the bar differential, giving
the classical bar complex $\barB(\mathfrak{g}_0)$ of the
finite-dimensional Lie algebra~$\mathfrak{g}_0$.

In both cases, the associated graded complex is the
Chevalley--Eilenberg / bar complex of a finite-dimensional Lie algebra.
By Arkhipov~\cite{Arkhipov97}, there is a natural quasi-isomorphism
\begin{equation}\label{eq:arkhipov-classical}
\Phi_0 \colon C^{\bullet}_{\mathrm{CE}}(\mathfrak{g}_0)
 \xrightarrow{\;\sim\;}
 \barB(\mathfrak{g}_0)
\end{equation}
given by the bar-CE comparison map: on generators,
$\Phi_0(x_1 \wedge \cdots \wedge x_n)
= [x_1 | \cdots | x_n]_{\mathrm{bar}}$
(the corresponding bar element), extended by the shuffle product
to all degrees. This is a classical result in homological algebra
(e.g., Loday--Vallette~\cite{LV12}, \S2.2): the bar complex and
the Chevalley--Eilenberg complex of a Lie algebra are
quasi-isomorphic via the antisymmetrization map.

\emph{Step~3: Spectral sequence comparison.}
The conformal weight filtration induces convergent spectral sequences:
\begin{align}
{}^{\mathrm{BRST}}E_1^{p,q}
 &= H^{p+q}\bigl(\mathrm{gr}^p\, \cA_{\mathrm{tot}}^{\mathrm{rel}}\bigr)
 \;\Longrightarrow\;
 H^{p+q}(Q_{\mathrm{BRST}}), \\
{}^{\mathrm{bar}}E_1^{p,q}
 &= H^{p+q}\bigl(\mathrm{gr}^p\, \barB^{\mathrm{ch}}_0(\cA_{\mathrm{tot}})\bigr)
 \;\Longrightarrow\;
 H^{p+q}(d_{\mathrm{bar}}).
\end{align}
Both spectral sequences converge because the filtrations are bounded
below (conformal weight $\geq 0$) and exhaustive (every element has
finite weight), and the complexes are complete with respect to the
filtration (the vertex algebra is $\mathbb{Z}_{\geq 0}$-graded by
conformal weight with finite-dimensional graded pieces).

The map $\Phi_0$ of Step~2 defines an isomorphism
${}^{\mathrm{BRST}}E_1^{p,q} \xrightarrow{\sim}
{}^{\mathrm{bar}}E_1^{p,q}$ at the $E_1$ page: at each conformal
weight~$p$, the associated graded complexes are identified by~$\Phi_0$,
which is a quasi-isomorphism.

\emph{Step~4: Lifting to a chain map.}
The assumed filtered lifting data promotes the $E_1$ comparison to a
map of filtered complexes. Once this filtered chain map is constructed,
the standard spectral sequence comparison theorem
(Eilenberg--Moore~\cite{EM66}; see also
Weibel~\cite[Theorem~5.2.12]{Weibel94}) implies that a filtered chain
map inducing an isomorphism on the $E_1$ page is a quasi-isomorphism.

Concretely, $\Phi$ is constructed inductively on filtration degree.
At level $N = 0$, $\Phi$ is the classical map~$\Phi_0$. At level~$N$,
given $\Phi|_{F^{\leq N-1}}$, one extends to $F^{\leq N}$ by solving
a lifting problem: the obstruction to extending lies in
$H^{n+1}(\mathrm{gr}^N\,\barB^{\mathrm{ch}}_0)$, which is the
$(n+1)$-st cohomology of the classical bar complex at weight~$N$.
The theorem assumes these obstruction classes vanish; in the standard
free-field and affine PBW cases this is the Koszul-resolution
acyclicity used in the preceding paragraph. The induction then proceeds.

The map $\Phi$ so constructed is a filtered chain map inducing an
isomorphism on $E_1$ pages. By the Eilenberg--Moore comparison
theorem, $\Phi$ is a quasi-isomorphism.
\end{proof}

\begin{remark}[BV/BRST reading of the master square]
\label{rem:bv-convergence}
\index{BV complex!convergence with bar complex}
Theorem~\ref{thm:brst-bar-genus0} compares the relative BRST complex
with the genus-$0$ chiral bar complex under the PBW lifting
hypotheses. It does not identify $\barB_X(\cA^!)$ with the ghost
complex. The ghost complex is the external BRST resolution determined
by the gauge symmetry and its chosen stress tensor; $\barB_X(\cA)$ is
the collision coalgebra; $\cA^!$ is obtained from the bar coalgebra by
Verdier duality on the Koszul locus; and
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)
=C^\bullet_{\mathrm{ch}}(\cA,\cA)$ is the chiral derived centre, the
closed-sector object. The master square therefore commutes on the relative
BRST locus $K_{\mathrm{BRST,tot}}=0$ after the filtered comparison
map~$\Phi$ is constructed, while the curvature square
$\dfib^{\,2}=\kappa(\cA)\omega_1$ belongs to the separate
lineage-specific bar curvature package.
\end{remark}

\begin{remark}[Low-degree shape of \texorpdfstring{$\Phi$}{Phi}]
\label{rem:brst-bar-explicit}
For the bosonic string $\cA = \mathcal{H}^{26}$, the chain map
$\Phi$ has the following low-degree associated-graded form. The
displayed ghost representatives live first in the absolute ghost Fock
model; the relative complex uses their $b_0$-horizontal projections.
\begin{itemize}
\item \emph{Degree~$0$}: $\Phi(|0\rangle) = 1 \in \barB^0$.
 A BRST-closed state of ghost number~$0$ maps to the unit in
 the bar complex.
\item \emph{Degree~$1$}: $\Phi(c_1 \alpha_{-1}^i |0\rangle)
 = [\alpha^i] \in \barB^1$, where $\alpha^i$ are the Heisenberg
 generators. The physical vertex operators (momentum eigenstates)
 map to bar generators.
\item \emph{Degree~$2$}:
$\Phi(\pi_{\mathrm{rel}}(c_0 c_1 |0\rangle)) = \eta_{12}$,
 where $\eta_{12} = d\log(z_1 - z_2)$ is the FM propagator.
 In the relative complex the state $c_0c_1|0\rangle$ is replaced
 by its $b_0$-horizontal representative; the formula records the
 associated-graded ghost--propagator identification, not a literal
 relative-chain equality.
\end{itemize}
In general, ghost insertions $c_{n_1} \cdots c_{n_k}$ map to
products of logarithmic forms $\eta_{i_1 j_1} \wedge \cdots \wedge
\eta_{i_r j_r}$ on the configuration space, with the precise
correspondence determined by the residue map of the FM propagator.
\end{remark}

\begin{corollary}[Physical anomaly cancellation at genus \texorpdfstring{$0$}{0};
\ClaimStatusConditional]
\label{cor:anomaly-physical-genus0-vol1}
\index{anomaly cancellation!BRST proof}
The genus-$0$ BRST anomaly cancellation is
$K_{\mathrm{BRST,tot}}=0$, equivalently
$c_{\mathrm{matter}}+c_{\mathrm{ghost}}=0$. On the Virasoro
stress-tensor lane this is the bar curvature-vanishing condition of
Theorem~\textup{\ref{thm:anomaly-koszul}}. Specifically:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $Q_{\mathrm{BRST}}^2 = 0$ on $\cA_{\mathrm{tot}}^{\mathrm{rel}}$
 if and only if $c(\cA) = 26$ \textup{(}Lemma~\textup{\ref{lem:brst-nilpotence})}.
\item $d_{\mathrm{bar}}^2 = 0$ on $\barB^{\mathrm{ch}}_0(\cA_{\mathrm{tot}})$
 on this stress-tensor lane if and only if
 $K_{\mathrm{BRST,tot}}=0$, i.e., $c(\cA)=26$
 \textup{(}Theorem~\textup{\ref{thm:anomaly-koszul})}.
\item The chain map $\Phi$ of Theorem~\textup{\ref{thm:brst-bar-genus0}}
 identifies both anomaly cancellation conditions under the PBW lifting
 hypotheses of that theorem: both sides are well-defined cochain
 complexes precisely when $c = 26$, and $\Phi$ is a quasi-isomorphism
 relating their cohomologies.
\end{enumerate}
\end{corollary}

\begin{proof}
Parts (i) and (ii) are the cited results. Part (iii):
Theorem~\ref{thm:brst-bar-genus0} constructs $\Phi$ under
the hypotheses $c = 26$ and filtered PBW lifting, giving a quasi-isomorphism that
identifies $H^*(Q_{\mathrm{BRST}}) \cong H^*(d_{\mathrm{bar}})$.
If $c \neq 26$, the BRST side has
\[
Q_{\mathrm{BRST}}^2
=\frac{c-26}{12}\sum_{n\in\mathbb Z}(n^3-n){:}c_{-n}c_n{:}\neq0
\]
as an operator on the full complex,
and the bar side has
$\dfib^{\,2}=K_{\mathrm{BRST,tot}}\cdot\omega_1
\cdot \mathrm{id} \neq 0$: neither is a cochain complex,
and both obstructions are controlled by the same numerical invariant
$c - 26$. The dictionary
\[
K_{\mathrm{BRST,tot}}
= K_{\mathrm{BRST}}(\cA_{\mathrm{matter}})
 + K_{\mathrm{BRST}}(\cA_{\mathrm{ghost}})
= \tfrac{c}{2} + \tfrac{-26}{2}
= \tfrac{c-26}{2}
\]
(Computation~\ref{comp:virasoro-curvature} for $\kappa(\mathrm{Vir}_c) = c/2$;
$K_{\mathrm{BRST}}(\text{$bc$-ghost}, \lambda{=}2)
=c_{\mathrm{gh}}/2=-13$)
converts the BRST obstruction $Q^2 \propto (c-26)$ into
the bar obstruction
$\dfib^{\,2}\propto K_{\mathrm{BRST,tot}}$ on this Virasoro lane.
\end{proof}

\begin{proposition}[Matched Koszul transport preserves BRST anomaly cancellation; \ClaimStatusConditional]
\label{prop:koszul-brst-anomaly-preservation-vol1}
\index{Koszul duality!BRST anomaly preservation}
\index{anomaly cancellation!Koszul duality}
Let $\cA_{\mathrm{tot}} = \cA_{\mathrm{matter}} \otimes \cA_{\mathrm{ghost}}$
be a BRST-quantized gauge system with total BRST conductor
$K_{\mathrm{BRST,tot}}
=K_{\mathrm{BRST}}(\cA_{\mathrm{matter}})
+K_{\mathrm{BRST}}(\cA_{\mathrm{ghost}})=0$.
Assume that the Koszul partner $\cA_{\mathrm{matter}}^!$ is equipped
with a compatible BRST stress tensor satisfying
\[
K_{\mathrm{BRST}}(\cA_{\mathrm{matter}}^!)
=-K_{\mathrm{BRST}}(\cA_{\mathrm{matter}}).
\]
Let $\widetilde{\cA}_{\mathrm{ghost}}$ be a transported ghost sector
whose BRST conductor satisfies
\[
K_{\mathrm{BRST}}(\widetilde{\cA}_{\mathrm{ghost}})
=-K_{\mathrm{BRST}}(\cA_{\mathrm{ghost}}).
\]
Then the dual total system
\[
 \cA_{\mathrm{tot}}^{\vee}
 \;=\; \cA_{\mathrm{matter}}^! \otimes \widetilde{\cA}_{\mathrm{ghost}}
\]
has vanishing total BRST conductor
\[
 K_{\mathrm{BRST}}(\cA_{\mathrm{tot}}^{\vee})
 \;=\; K_{\mathrm{BRST}}(\cA_{\mathrm{matter}}^!)
 + K_{\mathrm{BRST}}(\widetilde{\cA}_{\mathrm{ghost}})
 \;=\; -K_{\mathrm{BRST,tot}}
 \;=\; 0,
\]
and the BRST anomaly cancellation of
Corollary~\textup{\ref{cor:anomaly-physical-genus0-vol1}} holds for
$\cA_{\mathrm{tot}}^{\vee}$ at genus~$0$.
\end{proposition}

\begin{proof}
The BRST conductor is additive under tensor product because central
charges add. The two displayed hypotheses give
$K_{\mathrm{BRST}}(\cA_{\mathrm{matter}}^!)
=-K_{\mathrm{BRST}}(\cA_{\mathrm{matter}})$ and
$K_{\mathrm{BRST}}(\widetilde{\cA}_{\mathrm{ghost}})
=-K_{\mathrm{BRST}}(\cA_{\mathrm{ghost}})$, hence the total conductor
of $\cA_{\mathrm{tot}}^\vee$ is $-K_{\mathrm{BRST,tot}}=0$. The
genus-$0$ BRST cancellation follows from
Corollary~\ref{cor:anomaly-physical-genus0-vol1} applied to
$\cA_{\mathrm{tot}}^\vee$. No assertion is made that bar-cobar
reconstruction alone supplies the transported ghost sector or the
dual stress tensor.
\end{proof}

\begin{remark}[Scoping: why the ghost involution matters]
\label{rem:koszul-brst-scoping}
The hypothesis on $\widetilde{\cA}_{\mathrm{ghost}}$ is essential and
cannot be dropped. Consider the bosonic string:
$K_{\mathrm{BRST}}(\cA_{\mathrm{matter}})=13$ because
$c_{\mathrm{matter}}=26$, while the collision characteristic of the
same rank-$26$ Heisenberg algebra is
$\kappa(\mathcal H^{\oplus 26}_1)=26$. The $bc$ system at
$\lambda=2$ has
$c_{bc}=1-3(2{\cdot}2{-}1)^2=-26$ and
$K_{\mathrm{BRST}}(bc)=-13$, so
$K_{\mathrm{BRST,tot}}=13+(-13)=0$. A Koszul or Verdier operation on
the matter bar coalgebra does not automatically transform the
reparametrisation ghosts. If the ghost sector is kept fixed while the
matter stress tensor is replaced by a partner of conductor $-13$, the
new total conductor is $-13+(-13)=-26\neq0$, and BRST anomaly
cancellation fails. The proposition therefore requires an additional
ghost transport of conductor $+13$. This is an extra hypothesis on the
BRST package, not an internal self-duality of the $bc$ system and not
the Virasoro involution $c\mapsto26-c$.
\end{remark}

\begin{computation}[Superstring ghost/superghost Koszul dual;
\ClaimStatusConditional]
\label{comp:v1-superstring-ghost-koszul}
\index{superstring!ghost Koszul dual}
\index{$\beta\gamma$ system!superghost Koszul dual}
The bosonic string ghost system is the $bc$ pair at $\lambda = 2$
with $c_{bc} = 1 - 3(2{\cdot}2 - 1)^2 = -26$ and
$K_{\mathrm{BRST}}(bc)=c_{bc}/2=-13$. It is not Virasoro self-dual:
Virasoro self-duality is the same-family fixed point
$\mathrm{Vir}_c^!\simeq\mathrm{Vir}_{26-c}$, hence $c = 13$, whereas
the bosonic ghost sits at $c=-26$. The ghost transport required in
Remark~\ref{rem:koszul-brst-scoping} is a separate parity/Koszul
operation on the ghost package, not a Virasoro self-duality statement.

For the superstring, the ghost sector enlarges to
$(bc) \otimes (\beta\gamma)$, where the superghost
$\beta\gamma$ system sits at $\lambda = 3/2$. By the
formula $c_{\beta\gamma}(\lambda) = 2(6\lambda^2 - 6\lambda + 1)$,
\[
 c_{\beta\gamma}(\tfrac{3}{2})
 \;=\; 2\bigl(6 \cdot \tfrac{9}{4}
 - 6 \cdot \tfrac{3}{2} + 1\bigr)
 \;=\; 2\bigl(\tfrac{27}{2} - 9 + 1\bigr)
 \;=\; 2 \cdot \tfrac{11}{2}
 \;=\; 11,
\]
hence $K_{\mathrm{BRST}}(\beta\gamma)=c_{\beta\gamma}/2=11/2$, and
the transported dual satisfies
$K_{\mathrm{BRST}}((\beta\gamma)')=-11/2$.

The full superghost characteristic is
\[
 K_{\mathrm{BRST,ghost}}^{\mathrm{super}}
 \;=\; K_{\mathrm{BRST}}(bc) + K_{\mathrm{BRST}}(\beta\gamma)
 \;=\; -13 + \tfrac{11}{2}
 \;=\; -\tfrac{15}{2}.
\]
Superstring BRST anomaly cancellation requires
$K_{\mathrm{BRST,tot}} = K_{\mathrm{BRST,matter}}
+ K_{\mathrm{BRST,ghost}}^{\mathrm{super}} = 0$,
hence $K_{\mathrm{BRST,matter}} = 15/2$, equivalently
$c_{\mathrm{matter}} = 15$. For the $N = 1$ superconformal
matter of $d$ flat spacetime dimensions
($d$ free scalars contributing $d$ to $c$, plus $d$ free
Majorana fermions contributing $d/2$), this gives
$c_{\mathrm{matter}} = d + d/2 = 3d/2 = 15$, hence
$d = 10$: the critical dimension of the superstring. The
conductor sum for the transported superghost is
\[
 K_{\mathrm{BRST,ghost}}^{\mathrm{super}}
 + (K_{\mathrm{BRST,ghost}}^{\mathrm{super}})'
 \;=\; -\tfrac{15}{2} + \tfrac{15}{2}
 \;=\; 0,
\]
confirming that the superstring BRST anomaly cancellation
\textup{(}at $d = 10$\textup{)} is preserved by the matching
Koszul involution of Proposition~\ref{prop:koszul-brst-anomaly-preservation-vol1}.
\end{computation}

\begin{remark}[The ghost--superghost Koszul involution;
\ClaimStatusProvedElsewhere]
\label{rem:ghost-superghost-koszul}
\index{ghost!Koszul involution}
\index{superghost!Koszul involution}
The preceding computation identifies the ghost characteristic in
each of the two string backgrounds:
\begin{itemize}[nosep]
\item bosonic string: ghost $= bc$ at $\lambda = 2$, with
 $\kappa = -13$;
\item superstring: ghost $= bc$ at $\lambda = 2$ plus $\beta\gamma$
 at $\lambda = 3/2$, with total
 $K_{\mathrm{BRST}}=-15/2$.
\end{itemize}
In each case, anomaly preservation after matter dualization requires
a ghost transport that reverses the sign of the total ghost
characteristic while preserving the pairing used by the BRST
operator. For the $bc$ system this is not an internal same-family
self-duality: Friedan--Martinec--Shenker~\cite{FMS86} relate the
$bc$ and $\beta\gamma$ systems at bosonised level, and a parity-changed
ghost realization is the relevant opposite-characteristic model. For
the superstring combined ghost sector, the transport acts on the
combined $bc\otimes\beta\gamma$ package. The statement
$K_{\mathrm{BRST,ghost}}^{\mathrm{bos}} = -13$ and
$K_{\mathrm{BRST,ghost}}^{\mathrm{super}} = -15/2$ are the
numerical invariants before this transport, matching the standard
critical dimensions $d = 26$ and $d = 10$ of
Polchinski~\cite{Polchinski1998}. The involution is
\emph{not} the Virasoro self-duality at $c = 13$
\textup{(}which would require $\kappa + \kappa' = 13$\textup{)}:
the ghost transport is native to the $bc$\slash$\beta\gamma$ BRST
package and operates at a different locus.
\end{remark}

\begin{remark}[Higher genus]
\label{rem:brst-bar-higher-genus}
At genus $g \geq 1$, the BRST complex requires additional data:
the moduli-space density, gauge-fixing data, and
Costello renormalization framework~\cite{costello-renormalization} for
handling ultraviolet divergences. The bar complex side is well-defined
at all genera via configuration spaces on $\Sigma_g$
(Chapter~\ref{chap:higher-genus}). No all-genera chain map is
asserted here. Such a map would have to be genus-graded, compatible
with Costello's counterterm expansion, and square-zero only after the
curvature correction recorded in Theorem~\ref{thm:bv-bar-coderived-vol1};
it is not supplied by an unconstructed field-space measure.
The corresponding construction is recorded in
\S\ref{sec:modular-koszul-theory}.
\end{remark}

\section{Semi-infinite cohomology and the bar complex}
\label{sec:semi-infinite-bar}
\index{semi-infinite cohomology|textbf}

\subsection{Semi-infinite cohomology}

\begin{definition}[Semi-infinite cohomology {\cite{FGZ86}}]
\label{def:semi-infinite-cohomology}
\index{semi-infinite cohomology!definition}
Let $\widehat{L} = \bigoplus_{n \in \mathbb{Z}} L_n$ be a
$\mathbb{Z}$-graded Lie algebra with $\dim L_n < \infty$, and let
$M$ be a $\widehat{L}$-module. Write
$\widehat{L} = L_- \oplus L_0 \oplus L_+$ for the decomposition
into negative, zero, and positive modes. The \emph{semi-infinite
complex} is:
\[
C^{\infty/2+n}(\widehat{L}, M)
= M \otimes \textstyle\bigwedge\nolimits^{\infty/2+n}\! \widehat{L}^*
\]
where $\bigwedge^{\infty/2+n}$ denotes the semi-infinite wedge
power: the ``Dirac sea'' vacuum is the semi-infinite form
$\xi_0^* \wedge \xi_{-1}^* \wedge \xi_{-2}^* \wedge \cdots$
(wedging all negative-mode duals), and degree $n$ is measured
relative to this vacuum. The semi-infinite differential
$Q_{\mathrm{si}}$ combines the Chevalley--Eilenberg differential
with a ``charge anomaly'' correction term that ensures
$Q_{\mathrm{si}}^2 = 0$ without any restriction on the central charge.
The \emph{semi-infinite cohomology} is
$H^{\infty/2+\bullet}(\widehat{L}, M) =
H^*(C^{\infty/2+\bullet}(\widehat{L}, M), Q_{\mathrm{si}})$.
\end{definition}

\begin{remark}[Semi-infinite vs.\ string BRST]
\label{rem:semi-infinite-vs-brst}
The string BRST complex of \S\ref{sec:brst-bar-chain-map} couples
$\cA$ to $bc$-ghosts and requires $c = 26$ for $Q^2 = 0$
(Lemma~\ref{lem:brst-nilpotence}). Semi-infinite cohomology is
different: it is defined for any $\mathbb{Z}$-graded Lie algebra
$\widehat{L}$ and any module $M$, with $Q_{\mathrm{si}}^2 = 0$
unconditionally. The ghosts are ``built in'' to the semi-infinite
wedge product rather than introduced as an external $bc$-system.
For the string ($\widehat{L} = \mathrm{Vir}$, $M = \cA$),
semi-infinite cohomology of the Virasoro algebra \emph{does}
reduce to string BRST cohomology when $c = 26$~\cite{FGZ86}.
\end{remark}

\subsection{The bar--semi-infinite identification for Kac--Moody algebras}

\begin{theorem}[Bar complex = semi-infinite complex for KM;
\ClaimStatusConditional]
\label{thm:bar-semi-infinite-km}
\index{semi-infinite cohomology!bar complex identification}
\index{BRST!semi-infinite identification}
Let $\widehat{\fg}_k$ be the universal affine vertex algebra at level
$k \neq -h^\vee$. There is a quasi-isomorphism of filtered cochain
complexes:
\begin{equation}\label{eq:bar-semi-infinite}
\Psi \colon
 \bigl(\barB^{\mathrm{ch}}(\widehat{\fg}_k),\, d_{\mathrm{bar}}\bigr)
 \xrightarrow{\;\sim\;}
 \bigl(C^{\infty/2+\bullet}(\widehat{\fg}_k, V_k),\, Q_{\mathrm{si}}\bigr)
\end{equation}
identifying the chiral bar complex with the semi-infinite complex
\textup{(}with coefficients in the vacuum module $V_k$\textup{)}.
In particular:
\begin{equation}\label{eq:bar-equals-semi-infinite}
H^*(\barB^{\mathrm{ch}}(\widehat{\fg}_k))
\;\cong\;
H^{\infty/2+*}(\widehat{\fg}_k,\, V_k).
\end{equation}
\end{theorem}

\begin{proof}
The proof parallels that of
Theorem~\ref{thm:brst-bar-genus0}, replacing the string BRST
complex with the semi-infinite complex and removing the
$c = 26$ hypothesis.

\emph{Step~1: Conformal weight filtration.}
Both complexes carry bounded-below, exhaustive
$\mathbb{Z}_{\geq 0}$-filtrations by total conformal weight.
On the bar side, this is the PBW filtration of
Theorem~\ref{thm:brst-bar-genus0}, Step~1. On the semi-infinite
side, the conformal weight filtration arises from the
$L_0$-grading on $V_k$ and the mode grading on
$\bigwedge^{\infty/2+\bullet}\!\widehat{\fg}^*_k$. Both
differentials ($d_{\mathrm{bar}}$ and $Q_{\mathrm{si}}$) respect
these filtrations: $d_{\mathrm{bar}}$ preserves total conformal
weight (OPE residues preserve weight), and $Q_{\mathrm{si}}$
preserves it by construction~\cite{FGZ86}.

\emph{Step~2: Associated graded.}
On the associated graded $\mathrm{gr}\,F^\bullet$,
$\mathrm{gr}\,\barB^{\mathrm{ch}}(\widehat{\fg}_k)$ reduces
to the classical bar complex $\barB(\fg)$ of the
finite-dimensional Lie algebra $\fg$
(only the leading OPE pole survives, giving the Lie bracket),
while $\mathrm{gr}\,C^{\infty/2+\bullet}(\widehat{\fg}_k, V_k)$
reduces to the Chevalley--Eilenberg complex
$C^*_{\mathrm{CE}}(\fg, \mathbb{C})$
(the semi-infinite vacuum collapses to $\bigwedge^*\!\fg^*$
when mode corrections are dropped;
see~\cite{FGZ86}, Proposition~2.1).
Both associated graded complexes compute the Lie algebra cohomology
$H^*(\fg, \mathbb{C})$. The classical bar--CE comparison map
$\Phi_0$ of Arkhipov~\cite{Arkhipov97}
(cf.\ \eqref{eq:arkhipov-classical}) provides a natural
quasi-isomorphism $\barB(\fg) \xrightarrow{\sim}
C^*_{\mathrm{CE}}(\fg, \mathbb{C})$.

\emph{Step~3: Spectral sequence comparison.}
The conformal weight filtrations induce convergent spectral sequences
on both sides (bounded below, exhaustive, finite-dimensional
graded pieces). The map $\Phi_0$ induces an isomorphism at the
$E_1$ page. By the Eilenberg--Moore comparison theorem
(\cite{EM66}; cf.\ \cite[Theorem~5.2.12]{Weibel94}), $\Phi_0$ lifts
to a filtered chain map
$\Psi \colon \barB^{\mathrm{ch}}(\widehat{\fg}_k) \to
C^{\infty/2+\bullet}(\widehat{\fg}_k, V_k)$
that is a quasi-isomorphism.

\emph{Step~4: No anomaly obstruction.}
Unlike Theorem~\ref{thm:brst-bar-genus0}, no central charge
condition is needed. On the bar side, $d_{\mathrm{bar}}^2 = 0$
by the Arnold relations
(Theorem~\ref{thm:arnold-three}); the curvature
$m_0 = \kappa \cdot \mathbf{1}$ contributes to the $A_\infty$
structure but does not obstruct the bar differential. On the
semi-infinite side, $Q_{\mathrm{si}}^2 = 0$ by
construction~\cite{FGZ86}: the semi-infinite wedge product
absorbs the charge anomaly that would otherwise require
$c = 26$. Both differentials square to zero at every level
$k \neq -h^\vee$, and the spectral sequence comparison
applies without restriction.

The condition $k \neq -h^\vee$ ensures that the Sugawara
construction is well-defined, providing the $L_0$-grading
that drives the filtration. At critical level
$k = -h^\vee$, the Sugawara stress tensor is undefined, but the
semi-infinite complex is still defined using the loop rotation
grading; the identification at critical level follows from the
Feigin--Frenkel theorem~\cite{Feigin-Frenkel}
(cf.\ Theorem~\ref{thm:critical-level-structure}).
\end{proof}

\begin{remark}[String BRST as a special case of semi-infinite cohomology]
\label{rem:string-brst-special-case}
The string BRST comparison is the Virasoro analogue of
Theorem~\ref{thm:bar-semi-infinite-km}, not a literal specialization
of the affine Kac--Moody theorem. By~\cite{FGZ86}, the string BRST
complex of $\mathcal{H}^{26}\otimes bc$ with $c_{\mathrm{tot}}=0$ is
the semi-infinite complex of the Virasoro algebra acting on
$\mathcal{H}^{26}$. Under the PBW lifting hypotheses of
Theorem~\ref{thm:brst-bar-genus0}, the resulting Virasoro
semi-infinite comparison gives the map~$\Phi$. At
$c_{\mathrm{matter}}=26$, both the bosonic-string BRST anomaly
\[
\frac{c_{\mathrm{matter}}-26}{12}
\sum_{n\in\mathbb Z}(n^3-n){:}c_{-n}c_n{:}
\]
and $Q_{\mathrm{si}}^2$ vanish on the relative complex; away from
$c_{\mathrm{matter}}=26$, this quadratic ghost anomaly measures the
mismatch.
\end{remark}

\subsection{Anomaly duality from complementarity}

\begin{corollary}[Anomaly duality for Kac--Moody pairs;
\ClaimStatusConditional]
\label{cor:anomaly-duality-km-vol1}
\index{anomaly cancellation!Kac--Moody duality}
\index{Feigin--Frenkel duality!anomaly interpretation}
Let $\widehat{\fg}_k$ be an affine Kac--Moody algebra at generic
level $k$, with Feigin--Frenkel dual
$\widehat{\fg}_{k'} = \widehat{\fg}_{-k-2h^\vee}$. Then:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Bar cohomology = semi-infinite cohomology.}
The bar cohomology computations of
Part~\ref{part:characteristic-datum} \textup{(}Riordan numbers for
$\widehat{\mathfrak{sl}}_2$, the Hilbert series of
Theorem~\textup{\ref{thm:bar-cohomology-level-independence})}
are semi-infinite cohomology computations:
\[
\dim H^n(\barB^{\mathrm{ch}}(\widehat{\fg}_k))
= \dim H^{\infty/2+n}(\widehat{\fg}_k, V_k).
\]

\item \emph{Curvature = conformal anomaly.}
The genus-$1$ curvature coefficient
$\kappa(\widehat{\fg}_k) = (k+h^\vee)\dim\fg/(2h^\vee)$
\textup{(}Theorem~\textup{\ref{thm:genus-universality}(i))} equals
the semi-infinite anomaly coefficient. For affine Kac--Moody pairs,
the Feigin--Frenkel anti-symmetry
$\kappa(\widehat{\fg}_k) + \kappa(\widehat{\fg}_{-k-2h^\vee}) = 0$
of Theorem~\textup{\ref{thm:genus-universality}(ii)} is the
anomaly cancellation for the Feigin--Frenkel pair: the
conformal anomalies of $\widehat{\fg}_k$ and
$\widehat{\fg}_{-k-2h^\vee}$ cancel.
\textup{(}This anti-symmetry holds for KM/free-field families where the
duality is level-negating; it fails for Virasoro, where
$\kappa(\mathrm{Vir}_c) + \kappa(\mathrm{Vir}_{26-c}) = 13 \neq 0$.\textup{)}

\item \emph{Complementarity = anomaly duality.}
The quantum complementarity theorem
\textup{(}Theorem~\textup{\ref{thm:quantum-complementarity-main})}
applied to the Koszul pair
$(\widehat{\fg}_k, \widehat{\fg}_{-k-2h^\vee})$ gives:
\[
Q_g(\widehat{\fg}_k) \oplus Q_g(\widehat{\fg}_{-k-2h^\vee})
= H^*(\overline{\mathcal{M}}_g,\, Z(\widehat{\fg}_k)).
\]
Via the bar--semi-infinite identification, the left side is a
direct sum of semi-infinite cohomology spaces on
$\overline{\mathcal{M}}_g$: the genus-$g$ quantum corrections
of the WZW model at level~$k$ and its Feigin--Frenkel dual sum to
the full moduli space cohomology. This is the mathematical
content of anomaly cancellation for Kac--Moody pairs at all genera.

\item \emph{Universal MC duality.}
The universal Maurer--Cartan classes satisfy
$\Theta_{\widehat{\fg}_k} + \Theta_{\widehat{\fg}_{-k-2h^\vee}}
= 0$ (Theorem~\ref{thm:explicit-theta}), since
$\kappa(\widehat{\fg}_k) + \kappa(\widehat{\fg}_{-k-2h^\vee}) = 0$
by Theorem~\ref{thm:genus-universality}(ii).
The chain-level mechanism underlying~(c) is:
the Verdier involution exchanges
$\Theta_{\widehat{\fg}_k}$ and $-\Theta_{\widehat{\fg}_{k'}}$,
producing the Lagrangian splitting of
Theorem~\ref{thm:quantum-complementarity-main}.
\end{enumerate}
\end{corollary}

\begin{proof}
Part~(a) is the cohomology-level consequence of
Theorem~\ref{thm:bar-semi-infinite-km}. Part~(b): the
curvature $m_0 = \kappa \cdot \mathbf{1}$ in the bar complex
corresponds, under the quasi-isomorphism~$\Psi$, to the
semi-infinite anomaly (the failure of the naive CE differential
to square to zero, corrected by the semi-infinite charge).
The genus universality theorem identifies this with the
conformal anomaly coefficient. The KM anti-symmetry
$\kappa(\widehat{\fg}_k) + \kappa(\widehat{\fg}_{-k-2h^\vee}) = 0$
follows from the Feigin--Frenkel level shift and the formula
$\kappa = (k+h^\vee)\dim\fg/(2h^\vee)$: replacing $k$ by
$-k - 2h^\vee$ negates~$\kappa$.
Part~(c): combine the bar--semi-infinite identification with
Theorem~\ref{thm:quantum-complementarity-main}. The genus-$g$
obstruction space $Q_g(\widehat{\fg}_k)$ is the associated
graded of $H^*(\barB^{(g)}(\widehat{\fg}_k))$, which by
Theorem~\ref{thm:bar-semi-infinite-km} is the genus-$g$
semi-infinite cohomology. The complementarity sum equals
$H^*(\overline{\mathcal{M}}_g, Z(\widehat{\fg}_k))$ by
Theorem~\ref{thm:quantum-complementarity-main}.
\end{proof}

\begin{remark}[The Master Table, revisited]
\label{rem:master-table-brst}
\index{master table of invariants!BRST interpretation}
Via Corollary~\ref{cor:anomaly-duality-km-vol1}, every entry in the Master Table (Table~\ref{tab:master-invariants}) is a semi-infinite anomaly coefficient: $\kappa$ is the semi-infinite anomaly, $c + c' = 2\dim\fg$ the total Feigin--Frenkel anomaly, and $F_g$ the genus-$g$ WZW free energy.
\end{remark}

\subsection{Extension to $\mathcal{W}$-algebras via Drinfeld--Sokolov reduction}

\begin{theorem}[DS transport of bar = semi-infinite for principal \texorpdfstring{$\mathcal{W}$}{W}-algebras;
\ClaimStatusConditional]
\label{thm:bar-semi-infinite-w}
\index{semi-infinite cohomology!W-algebra identification}
\index{Drinfeld--Sokolov reduction!semi-infinite cohomology}
Let $\mathcal{W}^k(\fg, f_{\mathrm{prin}})$ be the principal
W-algebra at level $k \neq -h^\vee$. Assume that the affine
bar--semi-infinite quasi-isomorphism of
Theorem~\ref{thm:bar-semi-infinite-km} is compatible with principal
quantum Drinfeld--Sokolov reduction on the relevant filtered
complexes: the bar construction intertwines the DS BRST
differential up to filtered quasi-isomorphism, the semi-infinite
complex intertwines with the DS differential, and passage to DS
cohomology preserves the affine comparison map. Then there is a
quasi-isomorphism:
\begin{equation}\label{eq:bar-semi-infinite-w}
\barB^{\mathrm{ch}}(\mathcal{W}^k(\fg))
\;\xrightarrow{\;\sim\;}\;
C^{\infty/2+\bullet}(\mathcal{W}^k(\fg),\, M_k)
\end{equation}
where $M_k$ is the vacuum module for $\mathcal{W}^k(\fg)$ and the
right side is the semi-infinite complex defined with respect to the
conformal weight grading. In particular:
\[
H^*(\barB^{\mathrm{ch}}(\mathcal{W}^k(\fg)))
\;\cong\;
H^{\infty/2+*}(\mathcal{W}^k(\fg),\, M_k).
\]
\end{theorem}

\begin{proof}
Under the stated transport hypotheses, begin with the affine
quasi-isomorphism of Theorem~\ref{thm:bar-semi-infinite-km}. The
first compatibility assumption identifies the DS reduction of the
affine bar complex with
$\barB^{\mathrm{ch}}(\mathcal{W}^k(\fg))$, while the second
identifies the DS reduction of the affine semi-infinite complex with
$C^{\infty/2+\bullet}(\mathcal{W}^k(\fg), M_k)$. The third
assumption ensures that the affine comparison map survives passage to
DS cohomology. The resulting reduced map is exactly the displayed
quasi-isomorphism.
\end{proof}

\begin{corollary}[Virasoro bar complex = semi-infinite complex;
\ClaimStatusConditional]
\label{cor:virasoro-semi-infinite}
\index{semi-infinite cohomology!Virasoro}
\index{Virasoro algebra!semi-infinite cohomology}
For the Virasoro algebra $\mathrm{Vir}_c$ at central charge
$c = 1 - 6(k+1)^2/(k+2)$ \textup{(}obtained as
$\mathcal{W}^k(\mathfrak{sl}_2)$\textup{)}:
\[
H^*(\barB^{\mathrm{ch}}(\mathrm{Vir}_c))
\;\cong\;
H^{\infty/2+*}(\mathrm{Vir}_c,\, M_c)
\]
where $M_c$ is the vacuum Virasoro module. The Motzkin-number
bar cohomology dimensions of
Theorem~\textup{\ref{thm:virasoro-chiral-koszul}} are therefore
semi-infinite cohomology dimensions.
\end{corollary}

\begin{proof}
Apply Theorem~\ref{thm:bar-semi-infinite-w} with
$\fg = \mathfrak{sl}_2$, $f = f_{\mathrm{prin}}$.
\end{proof}

\begin{corollary}[Curvature complementarity for principal \texorpdfstring{$\mathcal{W}$}{W}-algebra pairs;
\ClaimStatusConditional]
\label{cor:anomaly-duality-w}
\index{anomaly cancellation!W-algebra duality}
Let $\mathcal{W}^k(\fg)$ be the principal W-algebra, with
Feigin--Frenkel same-family partner
$\mathcal{W}^{k'}(\fg) = \mathcal{W}^{-k-2h^\vee}(\fg)$.
Then:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The curvature coefficients satisfy the same
level-independent complementarity law as the central-charge
package. For principal finite-type $\mathcal{W}$-algebras,
\[
\kappa(\mathcal{W}^k(\fg)) + \kappa(\mathcal{W}^{k'}(\fg))
= \bigl(c(\mathcal{W}^k(\fg)) + c(\mathcal{W}^{k'}(\fg))\bigr)
\varrho(\fg),
\]
where $\varrho(\fg) = \sum_{i=1}^r \frac{1}{m_i+1}$ is the anomaly
ratio from Theorem~\ref{thm:wn-obstruction}. Thus the sum is a
level-independent constant: $13$ for Virasoro and $250/3$ for
$\mathcal{W}_3$.

\item Conditional on the same-family DS/bar transport clause of
Theorem~\ref{thm:w-algebra-koszul-main}, the quantum complementarity theorem
\textup{(}Theorem~\textup{\ref{thm:quantum-complementarity-main})}
applied to the W-algebra same-family Koszul pair
\textup{(}Theorem~\textup{\ref{thm:w-algebra-koszul-main})} gives:
\[
Q_g(\mathcal{W}^k) \oplus Q_g(\mathcal{W}^{-k-2h^\vee})
= H^*(\overline{\mathcal{M}}_g,\, Z(\mathcal{W}^k)).
\]
This is the genus-$g$ complementarity statement for the principal
$\mathcal{W}$-pair.

\item For $\fg = \mathfrak{sl}_2$
\textup{(}Virasoro\textup{)}: the Virasoro at
$c$ and its same-family shadow partner at $c' = 26 - c$ have
curvature coefficients adding to~$13$, and their
genus-$g$ quantum corrections sum to
 $H^*(\overline{\mathcal{M}}_g, Z(\mathrm{Vir}_c))$. Here
 $\mathrm{Vir}_{26-c}$ is the proved M/S-level shadow partner used in
 the semi-infinite calculation; the stronger H-level
 infinite-generator realization belongs to MC4
 (MC4 closed; Vol~I Theorem~\ref{thm:completed-bar-cobar-strong}).
\end{enumerate}
\end{corollary}

\begin{proof}
Combine Theorem~\ref{thm:wn-obstruction} with
Theorem~\ref{thm:central-charge-complementarity}: for the principal
finite-type $\mathcal{W}$-algebra,
$\kappa(\mathcal{W}^k(\fg)) = c(\mathcal{W}^k(\fg))\cdot\varrho(\fg)$.
Part~(b) then follows from the quantum complementarity theorem.
Part~(c): specialize to $\fg = \mathfrak{sl}_2$ with $h^\vee = 2$,
for which $c + c' = 26$ and $\varrho(\mathfrak{sl}_2)=1/2$.
\end{proof}

\begin{remark}[Conditional semi-infinite interpretation]
\label{rem:w-semi-infinite-conditional}
If Theorem~\ref{thm:bar-semi-infinite-w} holds, then
Corollary~\ref{cor:anomaly-duality-w} acquires the intended
semi-infinite anomaly interpretation for principal
$\mathcal{W}$-algebra pairs. This interpretation remains conditional
on explicit DS/bar compatibility.
\end{remark}

\section{Holomorphic-topological field theories}

The physical content (Gaiotto's framework, boundary chiral
algebras, HT boundary conditions, W-algebras from Higgs branches)
is in Volume~II\@. The BV algebra structure on the bar complex
from configuration-space geometry is in
\S\ref{sec:complete-bv-structure}.

% Labels preserved for cross-reference compatibility.
\label{rem:ht-from-n4-sym}%
\label{rem:boundary-chiral-algebra-bv}%
\label{rem:bar-cobar-ht-boundary}%
% conj:holographic-bar-cobar defined in genus_complete.tex
\label{rem:w-algebra-bar-cobar}%


\section{The BV algebra structure}
\label{sec:complete-bv-structure}

\subsection{BV algebra definition}

\begin{definition}[BV algebra]
\label{def:bv-algebra-complete}
\index{BV algebra|textbf}
A \emph{Batalin--Vilkovisky algebra} is a graded commutative algebra
$(A, \cdot)$ equipped with a degree-$+1$ operator
$\Delta\colon A \to A$ satisfying:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Nilpotency}: $\Delta^2 = 0$.
\item \emph{Second-order}: $\Delta$ is a second-order operator, meaning the
 \emph{BV bracket}
 \[
 \{a, b\} := (-1)^{|a|}\bigl[\Delta(ab) - \Delta(a)\,b
 - (-1)^{|a|} a\,\Delta(b)\bigr]
 \]
 (the failure of $\Delta$ to be a graded derivation) satisfies the
 graded Leibniz rule in each slot:
 \begin{gather*}
 \{a, bc\} = \{a, b\}\,c + (-1)^{(|a|+1)|b|} b\,\{a, c\},\\
 \{a, b\} = -(-1)^{(|a|+1)(|b|+1)}\{b, a\}.
 \end{gather*}
\end{enumerate}
The bracket automatically satisfies the graded Jacobi identity.
\end{definition}

\subsection{BV structure from configuration spaces}

\begin{theorem}[Conditional configuration-space BV package; \ClaimStatusConditional]
\label{thm:config-space-bv}
Assume that the diagonal-residue operator on the logarithmic bar
complex extends to a degree-$+1$ second-order operator
\[
\Delta\colon \bar{B}^{\mathrm{ch}}(\mathcal{A})
\longrightarrow
\bar{B}^{\mathrm{ch}}(\mathcal{A})[1]
\]
with $\Delta^2 = 0$, that the induced failure-of-derivation bracket is
the configuration-space residue pairing, and that these structures are
functorial in morphisms of chiral algebras. Then
$\bar{B}^{\mathrm{ch}}(\mathcal{A})$ carries a BV algebra structure
whose product is wedge product of logarithmic forms, whose bracket is
the residue pairing, and whose Laplacian is the diagonal-residue
operator.
\end{theorem}

\begin{proof}
Under the stated assumptions, the product is graded commutative by the
wedge-product sign rule, the bracket is generated from $\Delta$ by the
BV second-order identity, and the remaining BV axioms are exactly the
assumed nilpotence, Jacobi, and functorial compatibility conditions.
\end{proof}

\subsection{Quantum master equation}

\begin{remark}[Quantum master equation; \ClaimStatusHeuristic]
\label{rem:quantum-master-complete}%
The \emph{quantum master equation} is taken in the sign convention
of Appendix~\ref{app:signs}:
\[
\hbar \Delta_{\mathrm{BV}} S
+ \frac{1}{2}\{S,S\}_{\mathrm{BV}} = 0,
\]
equivalently $\Delta_{\mathrm{BV}} e^{S/\hbar}=0$ after the standard
exponential normalization. The bar side supplies the Maurer--Cartan
equation
$D\Theta+\frac{1}{2}[\Theta,\Theta]=0$. Identifying these equations
requires a BV Laplacian on the bar model and remains conditional on
Theorems~\ref{thm:config-space-bv} and~\ref{thm:bv-functor}.
\end{remark}

\begin{remark}[BV quantization and bar-cobar duality; \ClaimStatusHeuristic]
\label{rem:bv-equals-bar-cobar}%
Three operations must be kept separate. The BV or BRST complex computes
gauge-fixed physical cohomology. The bar complex computes the
collision coalgebra. The bar-cobar counit
\[
\Omega^{\mathrm{ch}}\barB^{\mathrm{ch}}(\mathcal{A})
\xrightarrow{\;\sim\;} \mathcal{A}
\]
is reconstruction on the Koszul locus; it does not produce
$\mathcal{A}^!$. The Koszul dual algebra enters through
Verdier duality applied to the bar coalgebra.

For affine Kac--Moody algebras, the proved statement is the filtered
comparison
\[
H^\bullet\!\bigl(\barB^{\mathrm{ch}}(\widehat{\fg}_k)\bigr)
\cong
H^{\infty/2+\bullet}(\widehat{\fg}_k,V_k)
\]
of Theorem~\ref{thm:bar-semi-infinite-km}, together with the separate
bar-cobar reconstruction of
Theorem~\ref{thm:bar-cobar-isomorphism-main}. For general chiral
algebras the BV reading remains heuristic unless a PBW filtration and
the conditional BV Laplacian package are supplied.
\end{remark}

\subsection{Summary: BV as functor}

\begin{theorem}[Conditional BV functor package; \ClaimStatusConditional]
\label{thm:bv-functor}
\index{BV functor}
Assume the conditional BV package of
Theorem~\ref{thm:config-space-bv} and a Verdier-duality comparison
identifying the dual of the bar coalgebra with a factorization algebra
$\cA^!_\infty$ compatibly with the bracket, coproduct/product, and
differential. Then the assignment
\[\mathrm{BV}: \mathrm{ChirAlg}_X \longrightarrow \mathrm{BV\text{-}Alg}\]
is a lax monoidal functor, and the Verdier dual
$\mathbb{D}_{\operatorname{Ran}}(\bar{B}(\mathcal{A}))$ identifies
with a factorization algebra $\cA^!_\infty$ whose underlying complex
is equivalent to $\bar{B}(\mathcal{A}^!)$
\textup{(}Theorem~\textup{\ref{thm:verdier-bar-cobar}}\textup{)}.
On the Koszul locus, $\cA^!_\infty \simeq \cA^!$.
\end{theorem}

\begin{proof}
Functoriality of the underlying bar construction is standard. The
extra BV functoriality and lax monoidal statements are exactly the
assumed functorial and tensor-compatibility properties of the
conditional BV package, while the Verdier-duality comparison is part
of the additional hypothesis in the theorem statement.
\end{proof}

\begin{remark}[Shifted symplectic structure from BV]\label{rem:bv-shifted-symplectic}
\index{shifted symplectic!from BV}
Conditional on Theorems~\ref{thm:config-space-bv}
and~\ref{thm:bv-functor}, the BV bracket on
$\barB^{\mathrm{ch}}(\cA)$ would provide a bar-side
$(-1)$-shifted Poisson model for the deformation theory. The
unconditional shifted-symplectic statements used later in the
manuscript instead come from the Verdier pairing on
$C_g = R\Gamma(\overline{\mathcal{M}}_g,\mathcal{Z}(\cA))$
\textup{(}Proposition~\ref{prop:ptvv-lagrangian}\textup{)} and from
the ambient cyclic deformation formal moduli problem
\textup{(}Theorem~\ref{thm:ambient-complementarity-fmp}\textup{)}.
\end{remark}

\section{Resolution for the Heisenberg algebra at all genera}
\label{sec:bv-bar-heisenberg-all-genera}
\index{Heisenberg!BV/bar identification|textbf}
\index{BV algebra!bar complex identification!Heisenberg}

The free-field case proves the scalar free-energy identity
predicted by Conjecture~\ref{conj:master-bv-brst}
for the Heisenberg family. The proof uses four independent
arguments that all produce the same identity.

\begin{theorem}[BV $=$ bar for the Heisenberg at all genera;
\ClaimStatusConditional]
\label{thm:heisenberg-bv-bar-all-genera-vol1}
\index{Heisenberg!determinant-line scalar}
\index{Faber--Pandharipande number!BV/bar identification}
For the Heisenberg vertex algebra $\cH_\kappa$ at level
$\kappa \neq 0$ and for every genus $g \geq 1$:
\begin{equation}\label{eq:bv-bar-heisenberg}
F_g^{\mathrm{BV}}(\cH_\kappa)
\;=\; F_g^{\mathrm{bar}}(\cH_\kappa)
\;=\; \kappa \cdot \lambda_g^{\mathrm{FP}},
\end{equation}
where $\lambda_g^{\mathrm{FP}}
= \frac{2^{2g-1}-1}{2^{2g-1}} \cdot
\frac{|B_{2g}|}{(2g)!}$
is the Faber--Pandharipande intersection number
$\int_{\overline{\mathcal{M}}_{g,1}} \psi^{2g-2}\lambda_g$.
\end{theorem}

\begin{proof}
We give four independent proofs, each arriving at the same
identity by a different route. The first two are the primary
arguments; the third and fourth provide independent confirmation.

\medskip
\noindent\textbf{Preliminary: the bar side.}
Theorem~D gives $\mathrm{obs}_g(\cA) = \kappa(\cA)\cdot\lambda_g$
for every chirally Koszul algebra on the uniform-weight lane.
The Heisenberg $\cH_\kappa$ qualifies:
\begin{itemize}[nosep]
\item $\kappa(\cH_\kappa) = \kappa$ (the level);
\item single generator of conformal weight~$1$
 (uniform-weight, no cross-channel correction at any genus;
 Remark~\ref{rem:propagator-weight-universality});
\item class~G (Gaussian): the OPE $a(z)a(w) \sim \kappa/(z{-}w)^2$
 has only a double pole, so shadow depth $r_{\max} = 2$ and all
 higher shadow components $\mathfrak{C}, \mathfrak{Q}, \ldots$
 vanish.
\end{itemize}
Therefore
$F_g^{\mathrm{bar}}(\cH_\kappa) = \kappa \cdot \lambda_g^{\mathrm{FP}}$
at every genus $g \geq 1$. It remains to show that the BV free
energy agrees.

\medskip
\noindent\textbf{Path \textup{(a)}: Quillen anomaly + GRR.}
\index{Quillen metric!BV/bar proof|(}
The zero-mode-reduced gauge-fixed free-boson determinant-line scalar
on a compact Riemann surface~$\Sigma_g$ of genus~$g$ is defined by
the zeta-regularized determinant
\begin{equation}\label{eq:bv-partition-heisenberg}
Z_g^{\mathrm{det}}(\cH_\kappa;\,\Sigma_g)
= \bigl(\det\nolimits'_\zeta \bar\partial_{\Sigma_g}\bigr)^{-\kappa},
\end{equation}
where $\det'_\zeta$ denotes the zeta-regularized determinant
with the zero modes removed. This is the analytic determinant-line
model for the free BV Gaussian; no ordinary measure on the field space
is being asserted.
Apply GRR to the universal curve
$\pi\colon \overline{\mathcal{C}}_g
\to \overline{\mathcal{M}}_g$
for the structure sheaf~$\mathcal{O}$.

\emph{Step~1} \textup{(}Quillen anomaly\textup{)}.
The Quillen metric $h_Q$ on the determinant line bundle
$\det(R\pi_*\mathcal{O})$ over
$\overline{\mathcal{M}}_g$ has curvature
\[
\operatorname{curv}(h_Q)
= -2\pi i\, c_1(\mathbb{E}),
\]
where $\mathbb{E} = R^0\pi_*\omega_{\mathcal{C}/\mathcal{M}_g}$
is the Hodge bundle of rank~$g$ \cite{Quillen85}.

\emph{Step~2} \textup{(}Scaling\textup{)}.
For $\kappa$ copies of the free boson, the total
determinant line bundle is
$\det(R\pi_*\mathcal{O})^{\otimes\kappa}$
with curvature $\kappa \cdot c_1(\mathbb{E})$.

\emph{Step~3} \textup{(}GRR + family index\textup{)}.
By the Grothendieck--Riemann--Roch theorem:
\[
\operatorname{ch}(\mathbb{E})
= \pi_*\bigl(\operatorname{Td}(\omega_\pi)\bigr)
= g + \sum_{j \geq 1}
\frac{B_{2j}}{(2j)!}\,\kappa_{2j-1},
\]
where $\kappa_j = \pi_*(c_1(\omega_\pi)^{j+1})$ are the
Miller--Morita--Mumford classes. The genus-$g$ obstruction
class is $\kappa(\cH_\kappa)\cdot c_g(\mathbb{E})
= \kappa\cdot\lambda_g$,
and the generating function of the family index is
$\sum_{g \geq 1}\mathrm{obs}_g\,\hbar^{2g}
= \kappa\cdot(\hat{A}(i\hbar) - 1)$
\textup{(}Theorem~\ref{thm:family-index}\textup{)},
where $\hat{A}(x) = (x/2)/\sinh(x/2)$.

\emph{Step~4} \textup{(}Faber--Pandharipande\textup{)}.
The intersection number
\[
\int_{\overline{\mathcal{M}}_{g,1}}
\psi^{2g-2}\,\lambda_g
= \lambda_g^{\mathrm{FP}}
= \frac{2^{2g-1}-1}{2^{2g-1}}
\cdot \frac{|B_{2g}|}{(2g)!}
\]
is the Faber--Pandharipande formula~\cite{FP00}.
Combining Steps~1--4:
$F_g^{\mathrm{BV}}(\cH_\kappa)
= \kappa \cdot \lambda_g^{\mathrm{FP}}
= F_g^{\mathrm{bar}}(\cH_\kappa)$.
\index{Quillen metric!BV/bar proof|)}

\medskip
\noindent\textbf{Path \textup{(b)}: Selberg zeta function.}
\index{Selberg zeta function!BV/bar proof|(}
The D'Hoker--Phong determinant formula~\cite{DP86} expresses
the Laplacian determinant on a compact hyperbolic
surface~$\Sigma_g$ as
\begin{equation}\label{eq:dhoker-phong-det}
\det\nolimits'_\zeta(\Delta_{\Sigma_g})
= Z_{\mathrm{Sel}}(1;\Sigma_g)\cdot e^{c_g},
\end{equation}
where $Z_{\mathrm{Sel}}(s;\Sigma_g)
= \prod_{\gamma\, \text{prim.}} \prod_{n=0}^\infty
(1 - e^{-(s+n)\ell(\gamma)})$
is the Selberg zeta function, the product running
over primitive closed geodesics, and $c_g$ is a genus-dependent
spectral constant
\textup{(}Theorem~\ref{V2-thm:thqg-I-determinant-formula}\textup{)}.
The Heisenberg determinant-line scalar factorizes as
\begin{equation}\label{eq:heisenberg-selberg}
Z_g^{\mathrm{det}}(\cH_\kappa;\Sigma_g)
= \bigl(\det\operatorname{Im}\Omega\bigr)^{-\kappa/2}
\cdot Z_{\mathrm{Sel}}(1;\Sigma_g)^{-\kappa/2}
\cdot e^{-\kappa c_g/2},
\end{equation}
where $\Omega$ is the period matrix of~$\Sigma_g$
\textup{(}Corollary~\ref{V2-cor:thqg-I-heisenberg-selberg}\textup{)}.
The Mumford isomorphism
$\lambda = c_1(\det\mathbb{E})$ combined with the
Belavin--Knizhnik formula~\cite{BK86} gives
$\det\operatorname{Im}\Omega \sim |\vartheta|^2$ on
$\mathcal{M}_g$, so that the variation of~\eqref{eq:heisenberg-selberg}
over the moduli space produces a curvature form proportional
to $\kappa \cdot c_1(\mathbb{E})$. Extraction of
the top Chern class yields
$F_g^{\mathrm{BV}}(\cH_\kappa)
= \kappa \cdot \lambda_g^{\mathrm{FP}}$,
confirming~\eqref{eq:bv-bar-heisenberg} by a second route.
\index{Selberg zeta function!BV/bar proof|)}

\medskip
\noindent\textbf{Path \textup{(c)}: direct family index.}
\index{family index theorem!BV/bar proof|(}
Apply the Atiyah--Singer family index theorem
directly to $\bar\partial^{\oplus\kappa}$
on the universal curve $\pi \colon \overline{\mathcal{C}}_g
\to \overline{\mathcal{M}}_g$.
The family index of $\bar\partial$ in
$K^0(\overline{\mathcal{M}}_g)$ is $R\pi_*\mathcal{O}$,
and the Chern character of this virtual bundle is computed by GRR as
\[
\operatorname{ch}(R\pi_*\mathcal{O})
= 1 - g + \sum_{j \geq 1}
\frac{B_{2j}}{(2j)!}\,\kappa_{2j-1}.
\]
The $\hat{A}$-genus of the relative tangent bundle
$T_\pi = \omega_\pi^{-1}$ satisfies
$\hat{A}(T_\pi) = \operatorname{Td}(\omega_\pi)$
(since $\hat{A}$ and $\operatorname{Td}$ are related by
$\hat{A}(E) = e^{-c_1(E)/2}\operatorname{Td}(E)$, and for
a line bundle $L$,
$\hat{A}(L^{-1}) = \operatorname{Td}(L)$).
Therefore the generating function for the genus-$g$ contributions is
\[
\sum_{g \geq 1} F_g(\cH_\kappa)\,\hbar^{2g}
= \kappa \cdot \bigl(\hat{A}(i\hbar) - 1\bigr)
= \kappa \cdot \Bigl(\frac{\hbar/2}{\sin(\hbar/2)} - 1\Bigr)
\]
\textup{(}\S\ref{subsec:why-ahat}\textup{)}.
The Taylor coefficient at $\hbar^{2g}$ is
$\kappa \cdot \frac{(2^{2g-1}-1)\,|B_{2g}|}{2^{2g-1}\,(2g)!}
= \kappa \cdot \lambda_g^{\mathrm{FP}}$,
confirming~\eqref{eq:bv-bar-heisenberg} by a third route.
Note: Path~\textup{(a)} derives the same generating function
from the Quillen anomaly and then extracts coefficients; this path
arrives at the generating function from the family index theorem
without passing through the determinant line bundle.
\index{family index theorem!BV/bar proof|)}

\medskip
\noindent\textbf{Path \textup{(d)}: numerical verification.}
\index{multi-path verification!Heisenberg BV/bar}
At each genus $g = 1, \ldots, 15$, three independent
implementations produce the same rational number $\lambda_g^{\mathrm{FP}}$:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item the Bernoulli formula
 $\lambda_g^{\mathrm{FP}}
 = \frac{(2^{2g-1}-1)\,|B_{2g}|}{2^{2g-1}\,(2g)!}$;
\item the Taylor extraction of the $\hat{A}$-series
 $(\hbar/2)/\sin(\hbar/2) - 1
 = \sum_{g \geq 1} \lambda_g^{\mathrm{FP}}\,\hbar^{2g}$;
\item a direct computation of the Faber--Pandharipande
 intersection integral on $\overline{\mathcal{M}}_{g,1}$
 via the string/dilaton equation and Witten's conjecture.
\end{enumerate}
All three agree at every genus tested. Sample values:
$\lambda_1^{\mathrm{FP}} = 1/24$,
$\lambda_2^{\mathrm{FP}} = 7/5760$,
$\lambda_3^{\mathrm{FP}} = 31/967680$.
\textup{(}Verified in the compute layer:
\texttt{heisenberg\_bv\_bar\_proof.py}, $60$ tests.\textup{)}
\end{proof}

\begin{remark}[Why the Heisenberg is special]
\label{rem:heisenberg-bv-bar-scope}
\index{BV algebra!bar complex identification!scope}
Theorem~\ref{thm:heisenberg-bv-bar-all-genera-vol1} proves the
\emph{scalar} \textup{(}partition function\slash free energy\textup{)}
consequence predicted by
Conjecture~\ref{conj:master-bv-brst} for the Heisenberg
family at all genera.
The Heisenberg succeeds because it is class~G:
a single Gaussian channel, no interaction vertices, and
all moduli dependence controlled by the Quillen anomaly.
For non-free theories, the scalar identification requires
the shadow obstruction tower machinery
\textup{(}Theorem~D for uniform-weight algebras;
the multi-weight genus expansion for $W_N$\textup{)}.

What remains open, even for
free fields, is:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item the chain-level quasi-isomorphism between the BV complex and
 the bar complex at genus $g \geq 1$;
\item the identification of the BV Laplacian with the sewing
 operator on the bar complex;
\item the full quantum master equation as a chain-level identity
 in the modular deformation complex
 \textup{(}not just the scalar trace\textup{)}.
\end{enumerate}
The scalar identification is an index-theoretic statement
(the Euler characteristic of the BV complex equals the Euler
characteristic of the bar complex); the chain-level identification
is a quasi-isomorphism, which is strictly stronger.
\end{remark}

\begin{proposition}[Three chain-level obstructions and harmonic factorization;
\ClaimStatusProvedHere]
\label{prop:chain-level-three-obstructions}
\index{BV algebra!chain-level obstructions|textbf}
\index{chain-level BV/bar identification}
The proposed chain-level identification between the BV complex and
the bar complex at genus $g \geq 1$
faces three obstructions, controlled by the shadow depth together
with the separate harmonic higher-brace coherence data of the
algebra.
\begin{enumerate}[label=\textup{(\arabic*)},nosep]
\item \textbf{Propagator regularity.}
 The BV propagator $P(z,w) = \bar\partial^{-1}\delta(z,w)$
 is a distribution; the bar propagator
 $d\log E(z,w)$ is meromorphic.
 By Hodge decomposition, $P = d\log E + P_{\mathrm{ex}}
 + P_{\mathrm{harm}}$
 where $P_{\mathrm{ex}}$ is $\bar\partial$-exact
 and drops in Dolbeault cohomology.
 The harmonic part $P_{\mathrm{harm}}$ integrates to a
 moduli-dependent prefactor controlled by the Quillen anomaly.
 For the Heisenberg: resolved at all genera.
 For interacting theories: the smooth correction couples to
 the OPE, producing chain-level discrepancies.
\item \textbf{Moduli dependence.}
 Both the BV Green function and the bar prime form
 depend on the complex structure of~$\Sigma_g$.
 The Quillen anomaly formula relates
 $\operatorname{curv}(h_Q)$ to $c_1(\mathbb{E})$
 universally: this resolves moduli dependence for any algebra
 whose determinant-line scalar is determined by a zeta-regularized
 determinant.
\item \textbf{Higher-degree coupling through the harmonic propagator.}
 For non-Gaussian theories, the BV Laplacian contracts
 field-antifield pairs through interaction vertices.
 On the bar side, the sewing operator contracts bar
 generators through the Bergman kernel.
 When the OPE has cubic and higher poles, the BV contraction
 passes through interaction vertices, creating contributions
 that do not factor through the sewing kernel alone.
 \begin{itemize}[nosep]
 \item \emph{Class~G} \textup{(}Heisenberg\textup{)}: absent.
 No interaction vertices.
 \item \emph{Class~L} \textup{(}affine Kac--Moody\textup{)}:
 the cubic harmonic correction vanishes by the Jacobi identity
 $f^{ab[c}f^{d]be} = 0$.
 Shadow depth $r_{\max} = 3$ kills only the scalar
 $\Sigma$-coinvariant shadow invariants \(S_r\) for \(r\geq4\);
 it does not by itself kill all quartic or higher brace
 components before the shadow projection. Obstruction~\textup{(3)}
 is killed at every genus only under the corresponding harmonic
 higher-brace coherence condition.
 \item \emph{Class~C}
 \textup{(}$\beta\gamma$\textup{)}:
 conditional on harmonic decoupling.
 Although the quartic interaction vertex is nonzero
 \textup{(}shadow depth $r_{\max} = 4$\textup{)},
 the proved conclusion here is only the reduction: the first
 possible chain-level discrepancy is the quartic harmonic insertion,
 and its vanishing is exactly the harmonic-decoupling condition.
 The proposition does not prove that decoupling statement.
 \item \emph{Class~M}
 \textup{(}Virasoro, $\cW_N$\textup{)}:
 the naive ordinary chain-level comparison fails, but the
 quartic and higher interaction vertices produce a harmonic
 discrepancy that factors through the curvature:
 \[
\delta_r^{\mathrm{harm}}
\;\in\;
\operatorname{End}(H_g)\cdot m_0^{\lfloor r/2 \rfloor - 1}
\qquad\text{for every } r \geq 4.
 \]
 Hence the class~$\mathsf{M}$ obstruction is curvature-divisible
 even when it does not vanish chainwise.
 \end{itemize}
\end{enumerate}
\end{proposition}

\begin{proof}
Obstruction~(1): the Hodge decomposition
$P = P_{\mathrm{mer}} + P_{\mathrm{ex}} + P_{\mathrm{harm}}$
on $\Sigma_g$ is standard. The $\bar\partial$-exact part
$P_{\mathrm{ex}}$ vanishes in the Dolbeault cohomology
computing both the BV and bar homology.

Obstruction~(2): the Quillen anomaly formula
$\operatorname{curv}(h_Q) = -2\pi i\,c_1(\mathbb{E})$
\cite{Quillen85} is independent of the chiral algebra;
it depends only on the universal curve.

Obstruction~(3): let $H_g$ denote the harmonic summand of the
fiber model at genus~$g$. Hodge decomposition gives
\[
P_{\mathrm{BV}}
\;=\;
d\log E + [d_{\mathrm{fib}}, h] + P_{\mathrm{harm}},
\]
where $h$ is the Hodge homotopy and $P_{\mathrm{harm}}$ is the
harmonic projector. The commutator term contributes only a chain
homotopy, so the discrepancy between the BV differential and the
bar differential is concentrated in the harmonic part. Since the
curvature $m_0 = \kappa(\cA)\cdot\omega_g$ is central of
cohomological degree~$2$, the harmonic projector commutes with
every power of~$m_0$ on~$H_g$. A degree-$r$ harmonic discrepancy
must preserve the harmonic summand, lower the number of external
legs by pairs, and contribute even degree
$2\lfloor r/2 \rfloor - 2$. On~$H_g$ the only degree-compatible
central insertion with that degree is
$m_0^{\lfloor r/2 \rfloor - 1}$. Therefore
\[
\delta_r^{\mathrm{harm}}
\;\in\;
\operatorname{End}(H_g)\cdot m_0^{\lfloor r/2 \rfloor - 1}
\qquad\text{for every } r \geq 4.
\]
For class~G, there are no interaction vertices, so the harmonic
discrepancy vanishes. For class~L
\textup{(}affine Kac--Moody at non-critical level
$k \neq -h^\vee$\textup{)}, the interaction vertex is the
structure-constant tensor $f^{abc}$. The cubic harmonic
correction has the form
$\sum_c f^{abc}\cdot I_{\mathrm{harm}}(z_1,z_2)\cdot f^{cde}$,
where $I_{\mathrm{harm}}$ is the integral of the harmonic
propagator against the cubic vertex measure. Antisymmetry of
$f^{abc}$ and the Jacobi identity
$f^{abc}f^{cde} + \text{cyclic} = 0$ force this coefficient to
vanish. Shadow depth $r_{\max} = 3$ excludes scalar shadow
invariants \(S_r\) for \(r\geq4\), but it does not exclude
quartic or higher brace terms before the shadow projection; their
ordinary chain-level vanishing is the separate harmonic
higher-brace coherence input. For class~C
\textup{(}$\beta\gamma$\textup{)}, the quartic correction is the
first possible harmonic term. The ordinary chain-level coefficient
vanishes precisely under the additional harmonic-decoupling
condition, namely factorization of the harmonic insertion through the
composite free-field trace sector; this is a separate conditional
input and is not used in the proved classification above. For
class~M no cancellation identity forces
$c_r(\cA)$ to vanish, so the ordinary chain-level discrepancy
survives even though it is curvature-divisible.
\end{proof}

\begin{remark}[BV/bar identification for class~C:
conditional three-mechanism test; \ClaimStatusConditional]%
\label{rem:bv-bar-class-c-proof}%
\index{BV algebra!bar complex identification!class C|textbf}%
\index{$\beta\gamma$ system!BV/bar identification}%
\index{harmonic decoupling!role separation}%
The chain-level BV/bar identification
(Conjecture~\ref{conj:master-bv-brst})
for class~C algebras ($\beta\gamma$ systems) at genus~$1$ reduces to
the following harmonic-decoupling test. The test is not a proof of the
conjecture until the harmonic projector is shown to factor through the
free-field trace sector.
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item \emph{OPE structure.}
 The $\beta\gamma$ OPE $\beta(z)\gamma(w)
 \sim 1/(z{-}w)$ has a simple pole only.
 The quartic interaction vertex arises not from the
 binary OPE (which is abelian: $\beta\beta \sim 0$,
 $\gamma\gamma \sim 0$) but from the composite field
 $:\!\beta\partial\gamma\!:$ coupling to the stress tensor
 $T = :\!\beta\partial\gamma\!:$, which is the source of the
 shadow depth $r_{\max} = 4$.
 The harmonic-propagator correction at the quartic vertex
 therefore involves the composite source
 $:\!\beta\partial\gamma\!:$, not a fundamental cubic pole.
\item \emph{Hodge type.}
 The $\beta\gamma$ system has conformal weights
 $(h_\beta, h_\gamma) = (\lambda, 1{-}\lambda)$.
 The BV propagator's harmonic part $P_{\mathrm{harm}}$
 on $\Sigma_g$ is a $(0,1)$-form in
 $\bar\partial$-cohomology;
 the quartic vertex measure is built from holomorphic fields and their
 derivatives on the configuration space. This bidegree separation is an
 obstruction to a local scalar term, but it is not by itself a
 vanishing theorem on the compactified configuration space. The missing
 assertion is that the harmonic insertion has no boundary residue after
 the Fulton--MacPherson expansion.
\item \emph{Role separation.}
 The key structural feature distinguishing class~C from
 class~M: in the $\beta\gamma$ system, the field producing
 the quartic interaction ($T = :\!\beta\partial\gamma\!:$)
 is a \emph{composite} of the fundamental fields
 $\beta, \gamma$ that carry the propagator.
 The propagator sews $\beta$--$\gamma$ pairs;
 the quartic vertex is built from composites of those
 same pairs. The required decoupling statement is that, after expanding
 the harmonic correction in the fundamental fields, it factors through
 the genus-$1$ trace of the underlying free-field sector, whose scalar
 anomaly is already resolved.
 For class~M (Virasoro, $\cW_N$), the stress tensor $T$ is
 itself a fundamental generator with its own propagator channel;
 the quartic vertex involves $T$ coupling to $T$, and the
 harmonic correction does not factor through a free subsystem.
\end{enumerate}
Thus the genus-$1$ class~C statement is conditional on harmonic
decoupling: after the boundary-residue assertion is supplied, the
quartic harmonic-propagator correction vanishes despite the nonzero
quartic shadow $Q^{\mathrm{contact}}_{\beta\gamma}$. This is the local
model for the all-genera harmonic-decoupling hypothesis used in
Theorem~\ref{thm:bv-bar-coderived-vol1}: once every harmonic insertion
factors through the same composite free-field sector, the quartic and
higher chain-level corrections vanish. For class~$\mathsf{M}$, the
quartic harmonic discrepancy
$\delta_4^{\mathrm{harm}} \propto Q^{\mathrm{contact}} \cdot
\kappa / \mathrm{Im}(\tau)$ is not cancelled by the Fay trisecant
identity. Proposition~\ref{prop:chain-level-three-obstructions}
shows that the full harmonic discrepancy still factors through the
curvature, so Theorem~\ref{thm:bv-bar-coderived-vol1} identifies the
class~$\mathsf{M}$ BV and bar models in the coderived category even
though the naive strict chain-level comparison fails on the
uncompleted models.
\end{remark}

\begin{remark}[BV sewing at the chain level: class-by-class status;
 \ClaimStatusConditional]%
\label{rem:bv-sewing-chain-level-classes-vol1}%
\index{BV algebra!sewing operator identification|textbf}%
\index{sewing operator!BV Laplacian identification}%
\index{Bergman kernel!sewing contraction}%
The identification $\Delta_{\mathrm{BV}} = d_{\mathrm{sew}}$ at
the chain level asserts that the BV Laplacian and the bar sewing
operator agree as $(g,n) \to (g{+}1,n{-}2)$ operations on the
modular convolution algebra~$\gAmod$: both contract a pair of
inputs through the Bergman kernel $d\log E(z,w)$ along the
non-separating boundary divisor
$\delta^{\mathrm{ns}}\colon
\overline{\mathcal{M}}_{g,n+2} \to
\overline{\mathcal{M}}_{g+1,n}$.
Four complementary descriptions of this comparison
\textup{(}operator definition, spectral sequence, Heisenberg
extraction, modular operad\textup{)} lead to the following
class-by-class obstruction profile.
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lcl}
\toprule
Class & Chain-level status & Comment \\
\midrule
$\mathsf{G}$ \textup{(}Heisenberg\textup{)}
 & chain-level curved equivalence & no interaction vertices \\
$\mathsf{L}$ \textup{(}affine KM\textup{)}
 & chain-level curved equivalence & Jacobi kills the cubic harmonic term \\
$\mathsf{C}$ \textup{(}$\beta\gamma$\textup{)}
 & chain-level under harmonic decoupling & composite free-field factorization \\
$\mathsf{M}$ \textup{(}Virasoro, $\cW_N$\textup{)}
 & coderived equivalence; naive chain level false & harmonic correction survives but is curvature-divisible \\
\bottomrule
\end{tabular}
\end{center}
For class~$\mathsf{M}$, the quartic discrepancy
$\delta_4^{\mathrm{harm}} \propto Q^{\mathrm{contact}} \cdot
\kappa / \operatorname{Im}(\tau)$ is not a coboundary
in the ordinary chain complex. Proposition~\ref{prop:chain-level-three-obstructions}
shows that the full harmonic discrepancy is a sum of curvature
powers, and Theorem~\ref{thm:bv-bar-coderived-vol1} proves that the
resulting comparison cone is coacyclic in the sense of
Definition~\ref{def:coacyclic-fact}. The remaining open questions are
the filtered-completed refinement for class~$\mathsf{M}$
\textup{(}Remark~\ref{rem:bv-bar-class-m-frontier}\textup{)} and the
all-genera harmonic-decoupling verification for class~$\mathsf{C}$.
\end{remark}

\begin{proposition}[Harmonic factorization of higher bar differentials;
\ClaimStatusConditional]%
\label{prop:harmonic-factorization}%
\index{harmonic factorization|textbf}%
\index{bar complex!harmonic projection}%
\index{curvature!harmonic factorization through}%
Let~$\cA$ be a chirally Koszul algebra with curvature
$m_0 = \kappa(\cA)\cdot\omega_g$ at genus $g \geq 1$
\textup{(}cohomological degree~$+2$, central\textup{)}.
Let $d_{\mathrm{fib}}$ denote the fiber bar differential,
$H_g \subset \ker(d_{\mathrm{fib}})$ the harmonic subspace
of the Hodge decomposition, and
$P_{\mathrm{harm}} \colon V_g \twoheadrightarrow H_g$
the harmonic projector. For each $r \geq 2$, let
$\delta_r$ denote the degree-$r$ component of the discrepancy
between the BV differential and the bar differential, arising
from insertion of the harmonic propagator at
$r$-valent interaction vertices. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The harmonic projection
$\delta_r^{\mathrm{harm}}
:= P_{\mathrm{harm}} \circ \delta_r \big|_{H_g}$
factors through powers of the curvature:
\[
\delta_r^{\mathrm{harm}}
\;=\;
\epsilon_r(\cA)\circ m_0^{\lfloor r/2 \rfloor - 1}
\qquad\text{for every } r \geq 2,
\]
for some central degree-zero endomorphism
$\epsilon_r(\cA)\in \operatorname{End}(H_g)$. The scalar
coefficient $c_r(\cA)$ denotes only the scalar/vacuum-channel
projection of~$\epsilon_r(\cA)$.
\item On the scalar/vacuum channel at low degrees:
$c_2(\cA) = 0$ \textup{(}the binary discrepancy is absorbed
by the Hodge homotopy\textup{)};
$c_3(\cA) = 0$ for classes~$\mathsf{G}$ and~$\mathsf{L}$
\textup{(}vanishes by the Jacobi identity for affine
Kac--Moody; absent for Heisenberg\textup{)};
$c_4(\cA) = S_4(\cA)$, the quartic shadow invariant.
\item For class~$\mathsf{G}$, $c_r(\cA) = 0$ for all $r$.
For class~$\mathsf{L}$, $c_r(\cA) = 0$ for all $r$
\textup{(}shadow depth $r_{\max} = 3$, so $c_r = 0$ for $r \geq 4$;
and $c_3 = 0$ by Jacobi\textup{)}.
For class~$\mathsf{M}$ \textup{(}Virasoro, $\cW_N$\textup{)},
the scalar/vacuum-channel coefficients $c_r(\cA)$ are generically
nonzero for $r \geq 4$, so the divisibility exponent cannot be
lowered on that channel.
\end{enumerate}
\end{proposition}

\begin{proof}
The proof proceeds through Hodge decomposition, degree
counting on the harmonic subspace, and centrality of the
curvature.

\emph{Step~1: Hodge decomposition isolates the harmonic
discrepancy.}
At genus $g \geq 1$, the Hodge decomposition of the BV
propagator is
\[
P_{\mathrm{BV}}
\;=\;
d\log E + [d_{\mathrm{fib}}, h] + P_{\mathrm{harm}},
\]
where $d\log E$ is the bar propagator \textup{(}the prime
form\textup{)}, $h$ is the Hodge homotopy, and
$P_{\mathrm{harm}}$ projects onto the harmonic
subspace~$H_g$. The commutator $[d_{\mathrm{fib}}, h]$
is $d_{\mathrm{fib}}$-exact and therefore contributes
only a chain homotopy: replacing $P_{\mathrm{BV}}$ by
$d\log E + P_{\mathrm{harm}}$ changes the BV differential
by a chain-homotopic deformation. The discrepancy between
the BV differential and the bar differential is therefore
concentrated in the harmonic part $P_{\mathrm{harm}}$.

\emph{Step~2: Centrality of $m_0$ on $H_g$.}
The curvature $m_0 = \kappa(\cA) \cdot \omega_g$
is central: it commutes with all operations in the fiber
model. In particular, $m_0$ commutes with the harmonic
projector $P_{\mathrm{harm}}$ and preserves the
decomposition
$V_g = \operatorname{im}(d_{\mathrm{fib}})
\oplus H_g \oplus \operatorname{im}(d_{\mathrm{fib}}^*)$.
The restriction of any power $m_0^k$ to~$H_g$ is again
central and has cohomological degree~$2k$.

\emph{Step~3: Degree counting.}
The degree-$r$ harmonic discrepancy
$\delta_r^{\mathrm{harm}}
= P_{\mathrm{harm}} \circ \delta_r |_{H_g}$
is a map from harmonics to harmonics. The $r$-valent
interaction vertex involves $r$ external legs from the fiber.
Insertion of the harmonic propagator contracts these legs
pairwise: each contraction through $P_{\mathrm{harm}}$
pairs two fiber directions and contributes cohomological
degree~$+2$. With $r$ legs, at most
$\lfloor r/2 \rfloor$ pairwise contractions are possible.
One contraction is already accounted for by the propagator
insertion that creates the discrepancy~$\delta_r$ itself.
The remaining $\lfloor r/2 \rfloor - 1$ contractions
contribute total cohomological degree
$2(\lfloor r/2 \rfloor - 1)$ to the harmonic-to-harmonic
map.

The degree count does \emph{not} imply that the residual
harmonic endomorphism is scalar. What it proves is the
divisibility statement: after the one propagator insertion
that creates~$\delta_r$, every remaining paired harmonic
contraction contributes a curvature factor. Thus there is a
central degree-zero endomorphism
$\epsilon_r(\cA)\in\operatorname{End}(H_g)$ such that
\[
\delta_r^{\mathrm{harm}}
\;=\;
\epsilon_r(\cA)\circ m_0^{\lfloor r/2 \rfloor - 1}.
\]
Identifying $\epsilon_r(\cA)$ with a scalar multiple of the
identity requires the separate vacuum-proportionality package
proved on the completed class-$\mathsf{M}$ surface in
Proposition~\ref{prop:central-m0-vacuum-proportionality}; it is not
assumed in this broad curvature-divisibility proposition.

\emph{Step~4: Low-degree evaluations.}
At $r = 2$: $\lfloor 2/2 \rfloor - 1 = 0$, so the scalar
channel of $\epsilon_2(\cA)$ is $c_2(\cA)$.
The binary discrepancy arises from replacing one bar
propagator by $P_{\mathrm{harm}}$. But the Hodge homotopy
$[d_{\mathrm{fib}}, h]$ already absorbs this replacement
at the binary level: the chain-homotopy equivalence between
$P_{\mathrm{BV}}$ and $d\log E$ at a single vertex
is the content of Step~1 applied at degree~$2$. Therefore
$c_2(\cA) = 0$.

At $r = 3$: $\lfloor 3/2 \rfloor - 1 = 0$, so the scalar
channel of $\epsilon_3(\cA)$ is $c_3(\cA)$.
For class~$\mathsf{G}$ \textup{(}Heisenberg\textup{)},
no cubic vertex exists, so $c_3 = 0$.
For class~$\mathsf{L}$ \textup{(}affine Kac--Moody at
$k \neq -h^\vee$\textup{)}, the cubic harmonic correction
takes the form
$\sum_c f^{abc} \cdot I_{\mathrm{harm}} \cdot f^{cde}$,
where $f^{abc}$ are the structure constants. By
antisymmetry of $f^{abc}$ and the Jacobi identity
$f^{ab[c}f^{d]be} = 0$, this coefficient vanishes:
$c_3(\cA) = 0$.

At $r = 4$: $\lfloor 4/2 \rfloor - 1 = 1$, so
$\delta_4^{\mathrm{harm}}$ is divisible by~$m_0$. The quartic
harmonic correction is the first term involving a nontrivial
curvature power. Its scalar/vacuum-channel coefficient
$c_4(\cA)$ is determined by the quartic shadow
invariant: $c_4(\cA) = S_4(\cA)$, the degree-$4$
projection of the Maurer--Cartan class
$\Theta_\cA$ in the convolution algebra.
For class~$\mathsf{G}$ and class~$\mathsf{L}$
\textup{(}shadow depth $r_{\max} \leq 3$\textup{)},
$S_4(\cA) = 0$ and thus $c_4(\cA) = 0$.
For class~$\mathsf{M}$ \textup{(}Virasoro\textup{)},
$S_4(\mathrm{Vir}_c) = 10/[c(5c+22)] \neq 0$
at generic~$c$, confirming that the quartic harmonic
discrepancy is nontrivial.

\emph{Step~5: Class-by-class vanishing.}
For class~$\mathsf{G}$: no interaction vertices at
any degree, so the harmonic discrepancy vanishes for all
$r \geq 2$.
For class~$\mathsf{L}$: shadow depth $r_{\max} = 3$
implies the scalar-channel coefficient $c_r(\cA) = 0$ for $r \geq 4$
\textup{(}no scalar shadow vertex survives at degree
$\geq 4$\textup{)}, and Jacobi kills $c_3$.
For class~$\mathsf{M}$: the shadow tower does not
terminate \textup{(}Corollary~\ref{cor:virasoro-postnikov-nontermination}\textup{)},
so the scalar-channel coefficients $c_r(\cA)$ are generically
nonzero for $r \geq 4$. The broad conclusion needed here is
curvature-divisibility: every harmonic discrepancy factors through
$m_0^{\lfloor r/2 \rfloor - 1}$, while scalar sharpness belongs to
the separate completed/vacuum-proportionality package.
\end{proof}

\begin{theorem}[BV$=$bar in the coderived category;
\ClaimStatusConditional]%
\label{thm:bv-bar-coderived-vol1}%
\index{BV algebra!bar complex identification!coderived category|textbf}%
\index{coderived category!BV/bar identification|textbf}%
Let~$\cA$ be a chirally Koszul algebra. The genus-$0$ BV/bar
comparison is the chain-level quasi-isomorphism of
Theorem~\ref{thm:bv-bar-geometric}. For each genus
$g \geq 1$, let
\[
 f_g \colon
 C^{\bullet}_{\mathrm{BV}}(\cA, \Sigma_g)
 \longrightarrow
 B^{(g)}(\cA)
\]
be the comparison morphism of filtered curved
factorization models
obtained by replacing the BV propagator with its Hodge
decomposition relative to the bar propagator. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item for every genus $g \geq 0$,
\[
 C^{\bullet}_{\mathrm{BV}}(\cA, \Sigma_g)
 \;\simeq_{D^{\mathrm{co}}}\;
 B^{(g)}(\cA);
\]
\item if $\cA$ lies in class~$\mathsf{G}$ or~$\mathsf{L}$, then
 $f_g$ is a weak equivalence of filtered curved models in the sense
 of Definition~\ref{def:curved-weak-equiv};
\item if $\cA$ lies in class~$\mathsf{C}$ and harmonic decoupling
 holds, then $f_g$ is a weak equivalence of filtered curved models;
\item if $\cA$ lies in class~$\mathsf{M}$, then for every $r \geq 4$
 the harmonic discrepancy satisfies
\[
 \delta_r^{\mathrm{harm}}
 \;\in\;
 \operatorname{End}(H_g)\cdot m_0^{\lfloor r/2 \rfloor - 1}
\]
and the cone of $f_g$ is coacyclic.
\end{enumerate}
\end{theorem}

\begin{proof}
At genus~$0$, the comparison is the chain-level quasi-isomorphism
of Theorem~\ref{thm:bv-bar-geometric}.

For $g \geq 1$, Hodge decomposition writes the BV propagator as
\[
P_{\mathrm{BV}}
\;=\;
d\log E + [d_{\mathrm{fib}}, h] + P_{\mathrm{harm}}.
\]
The commutator term contributes only a chain homotopy, so the
failure of~$f_g$ to intertwine the two curved differentials is the
harmonic discrepancy
$\delta^{\mathrm{harm}} = \sum_{r \geq 4}\delta_r^{\mathrm{harm}}$.
Proposition~\ref{prop:harmonic-factorization} gives the
curvature-divisibility
$\delta_r^{\mathrm{harm}} \in \operatorname{End}(H_g)\cdot
m_0^{\lfloor r/2 \rfloor - 1}$, and
Proposition~\ref{prop:chain-level-three-obstructions} gives the
class-by-class description of the scalar-channel coefficients.

If $\cA$ lies in class~$\mathsf{G}$ or~$\mathsf{L}$, all harmonic
discrepancies vanish by
Proposition~\ref{prop:harmonic-factorization}(iii).
Hence $f_g$ intertwines the curved
differentials on the nose. On the PBW-associated graded, the map is
the genus-$0$ comparison on each weight piece, hence a
quasi-isomorphism. By Definition~\ref{def:curved-weak-equiv}, $f_g$
is a weak equivalence of filtered curved models. The same argument
applies to class~$\mathsf{C}$ under harmonic decoupling.

Now assume $\cA$ lies in class~$\mathsf{M}$, and let
$K_g := \operatorname{cone}(f_g)$. By
Proposition~\ref{prop:chain-level-three-obstructions}, every
filtration quotient of~$K_g$ is annihilated by a power of the
central curvature~$m_0$. If $m_0 = 0$, the same proposition gives
$\delta_r^{\mathrm{harm}} = 0$ for all $r \geq 4$, so there is no
class~$\mathsf{M}$ discrepancy. If $m_0 \neq 0$, each
$m_0$-power-torsion quotient is resolved by the one-variable
$m_0$-Koszul complex, whose totalization is exact; by
Definition~\ref{def:coacyclic-fact}, these totalizations are
coacyclic. Since the coacyclic subcategory is thick and closed
under extensions,~$K_g$ itself is coacyclic. Therefore~$f_g$
becomes an isomorphism in the coderived quotient
\[
D^{\mathrm{co}}(B^{(g)}(\cA)\text{-}\mathrm{CoFact})
\;=\;
\mathrm{Hot}(B^{(g)}(\cA)\text{-}\mathrm{CoFact})
\big/\mathrm{Acycl}^{\mathrm{co}}_{\mathrm{fact}}
\]
of Definition~\ref{def:coderived-fact}. This is the required
coderived comparison. The provisional localization is not needed
for the argument.
\end{proof}

\begin{remark}[Harmonic mechanism behind the coderived comparison]
\label{rem:bv-bar-coderived-higher-genus}%
\index{coderived category!higher-genus validity}%
The curvature-divisibility relation
$\delta_r^{\mathrm{harm}} \in \operatorname{End}(H_g)\cdot
m_0^{\lfloor r/2 \rfloor - 1}$
\textup{(}Proposition~\ref{prop:harmonic-factorization}\textup{)}
is the genus-independent mechanism behind
Theorem~\ref{thm:bv-bar-coderived-vol1}. The proof has two inputs:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item Hodge decomposition on the fiber model isolates the harmonic
 part of the discrepancy, and the harmonic projector commutes with
 powers of the central curvature by degree counting on the harmonic
 summand.
\item The only degree-compatible harmonic insertion is through the
 curvature direction
 $m_0 = \kappa(\cA)\cdot\omega_g$, so the full discrepancy is
 $m_0$-power torsion and its cone is coacyclic in the sense of
 Definition~\ref{def:coacyclic-fact}.
\end{enumerate}
What remains open is the stronger vanishing of the scalar-channel
coefficients $c_r(\cA)$ in class~$\mathsf{M}$ and the all-genera
verification of harmonic decoupling in class~$\mathsf{C}$.
\end{remark}

\begin{remark}[Alternative approach via operadic Koszul duality]
\label{rem:bv-bar-coderived-operadic}%
\index{BV algebra!bar complex identification!operadic route}%
\index{Koszul duality!BV/bar comparison}%
There is a second route to
Theorem~\ref{thm:bv-bar-coderived-vol1}. By
Principle~\ref{princ:sc-two-incarnations}, the ordered bar complex
$\barB^{\mathrm{ord}}(\cA)$ is the open
$\Eone$-chiral coalgebra engine, while the derived center
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)
= C^{\bullet}_{\mathrm{ch}}(\cA,\cA)$ is the closed object carrying
the $\mathsf{SC}^{\mathrm{ch,top}}$ structure. In this two-coloured
package, the BV operator $\Delta_{\mathrm{BV}}$ is the closed-colour
contraction induced by the Swiss-cheese pairing, whereas the bar
differential $d_{\barB}$ is the open-colour coderivation induced by
the chiral product. The two operators therefore come from the same
operadic bar-cobar datum, but they live in different colours. What is
compared is not ``the bar complex as a Swiss-cheese algebra'': the
Swiss-cheese object is the pair
\[
\bigl(Z^{\mathrm{der}}_{\mathrm{ch}}(\cA),\,\cA\bigr),
\]
and the ordered bar complex enters as the open-colour coalgebra model
used to resolve the boundary algebra.

There is also a conditional operadic derivation of the coderived
comparison. Its input is not classical Swiss-cheese Koszulity by
itself. One must import the full
$\mathsf{SC}^{\mathrm{ch,top}}$ homotopy-Koszulity package recorded in
Remark~\ref{rem:homotopy-koszulity-center}: classical Swiss-cheese
Koszulity, the fixed formality comparison from the chiral closed
colour to the classical $E_2$ closed colour, and transfer through
bar-cobar quasi-isomorphisms. Together with the explicit description
of the Koszul dual cooperad in
Proposition~\ref{prop:sc-koszul-dual-three-sectors} and the center
identification of Theorem~\ref{thm:operadic-center-hochschild}, this
package gives a second proof route: the general bar-cobar
correspondence for Koszul coloured operads identifies the
$\mathsf{SC}^{\mathrm{ch,top}}$-algebra pair
\[
\bigl(Z^{\mathrm{der}}_{\mathrm{ch}}(\cA),\,\cA\bigr)
\]
with its
$\mathsf{SC}^{\mathrm{ch,top},!}$-coalgebra resolution in the coderived
category. On the closed side this resolution computes the BV operator
through the Swiss-cheese contraction; on the open side it computes the
bar differential through the cofree ordered bar coalgebra. Thus the
BV/bar comparison in $D^{\mathrm{co}}$ is the Swiss-cheese instance of
operadic Koszul duality. From this viewpoint,
Theorem~\ref{thm:bv-bar-coderived-vol1} is, conditional on that
imported homotopy-Koszulity package, the Swiss-cheese instance of the
general curved Koszul principle: off the strict locus, curvature
forces passage to $D^{\mathrm{co}}$, but the comparison cone is
invisible there.

This also isolates the class~$\mathsf{M}$ gap in operadic terms. The
coderived equivalence survives because the operadic quasi-isomorphism
still exists after passing to the Koszul resolution, but a strict
chain-level quasi-isomorphism on the explicit models requires the
transferred $\mathsf{SC}^{\mathrm{ch,top}}$ structure to collapse to a
formal one. That collapse holds for classes~$\mathsf{G}$ and
$\mathsf{L}$, is the harmonic-decoupling input in class~$\mathsf{C}$,
and is not available for class~$\mathsf{M}$, where the
higher transferred operations remain visible. The class~$\mathsf{M}$
obstruction is therefore not a failure of coderived Koszul duality; it
is the failure of the operadic quasi-isomorphism to descend to a
strict chain-level quasi-isomorphism on a non-formal explicit model.
\end{remark}

\begin{remark}[Why the coderived category is inevitable]
\label{rem:bv-bar-coderived-why}
\index{coderived category!physical inevitability}
\index{BV algebra!bar complex identification!physical interpretation}
The passage from the ordinary derived category to the coderived
category is not a technical convenience but a physical necessity,
and its inevitability can be understood from three complementary
viewpoints.

\emph{The worldsheet viewpoint.}
On a genus-$g$ Riemann surface $\Sigma_g$, the worldsheet path
integral produces amplitudes via the sewing construction: one cuts
$\Sigma_g$ along a collar into two pieces and sums over a complete
set of intermediate states. The sewing sum introduces the
propagator $P = P_{\mathrm{bar}} + P_{\mathrm{exact}} +
P_{\mathrm{harm}}$, where $P_{\mathrm{harm}}$ is the harmonic
piece from $H^{0,1}(\Sigma_g)$. The BV formalism uses the
\emph{full} propagator; the bar complex uses only
$P_{\mathrm{bar}} = d\log E(z,w)$. The discrepancy at degree~$r$
is controlled by the harmonic piece. This shows why curvature
appears in higher genus: the harmonic sector is invisible to the
genus-$0$ bar differential but survives in the BV propagator.
Passing to the coderived setting is therefore natural once
$d^2 = m_0 \cdot \mathrm{id}$ enters the picture. Theorem~\ref{thm:bv-bar-coderived-vol1}
supplies the missing step: curvature factorization forces the
comparison cone to be coacyclic.

\emph{The spacetime viewpoint.}
In the Costello--Li framework of twisted supergravity, the bulk
theory on $\mathrm{AdS}_{d+1}$ is computed by Witten diagrams
using the bulk propagator, while the boundary theory is computed
by the bar complex using the boundary OPE. The mismatch between
bulk and boundary propagators at one loop ($g = 1$) is the
holographic anomaly: the Weyl anomaly coefficient
$a - c$ in $4d$ becomes, on the algebraic side, a harmonic
correction to the BV/bar comparison. The coderived formalism
packages this anomaly as curvature data rather than forcing a
strict differential. Theorem~\ref{thm:bv-bar-coderived-vol1} shows that
the comparison map becomes an isomorphism after localizing at
coacyclic objects.

\emph{The categorical viewpoint.}
The coderived category $D^{\mathrm{co}}(\cA)$ is the natural
home for curved dg~algebras: it is the homotopy category of
dg~comodules over the bar coalgebra $B(\cA)$ in which
$d^2 = m_0 \cdot \mathrm{id}$ is permitted. The bar complex
$B(\cA)$ always satisfies $D_B^2 = 0$ (the total bar differential
squares to zero regardless of curvature), so $B(\cA)$ lives
natively in $D^{\mathrm{co}}$. The BV complex, with its
$d^2_{\mathrm{BV}} = \kappa \cdot \omega_g$ at genus~$g$,
satisfies the same curved relation. The coderived
category is the minimal ambient in which both objects are
well-defined. The ordinary derived
category, which requires $d^2 = 0$, is too restrictive: it
forces a choice of ``strictification'' (lifting the curvature
into the differential via a Maurer--Cartan twist), and different
choices produce inequivalent chain complexes. The coderived
category avoids this choice. By
Definitions~\ref{def:coacyclic-fact} and~\ref{def:coderived-fact},
curved objects are not set to zero in this localization; the
comparison map of Theorem~\ref{thm:bv-bar-coderived-vol1} becomes an
isomorphism precisely because its cone is coacyclic.

Thus the BV quantisation of the worldsheet sigma model and the
algebraic bar construction of the boundary vertex algebra live in the
same curved homological framework. The chain-level discrepancy for
class~$\mathsf{M}$ is therefore not a signal that the coderived
category is unnecessary; it is the reason the coderived category is
the correct ambient. What remains open is
the filtered-completed refinement in class~$\mathsf{M}$
\textup{(}Remark~\ref{rem:bv-bar-class-m-frontier}\textup{)} and the
all-genera harmonic-decoupling statement in class~$\mathsf{C}$.
\end{remark}

\begin{remark}[Class~$\mathsf{M}$ spectral and completed MC5]
\label{rem:bv-bar-class-m-frontier}
\index{BV algebra!class M frontier|textbf}%
\index{coderived category!filtered-completed refinement}%
Theorem~\ref{thm:bv-bar-coderived-vol1} and
Proposition~\ref{prop:chain-level-three-obstructions} isolate not
only the surviving coderived statement but also the exact reason the
strict chain-level form of MC5 fails for class~$\mathsf{M}$. For
Virasoro and principal $\cW_N$, the higher harmonic discrepancies
satisfy
\[
\delta_r^{\mathrm{harm}}
\;\in\;
\operatorname{End}(H_g)\cdot m_0^{\lfloor r/2 \rfloor - 1}
\qquad (r \geq 4).
\]
Corollary~\ref{cor:virasoro-postnikov-nontermination} shows that the
shadow obstruction tower does not terminate: the permanent cubic
source regenerates nonzero higher obstructions at every stage. In the
operadic language of
Remark~\ref{rem:bv-bar-coderived-operadic}, the transferred
class~$\mathsf{M}$ $A_\infty$-operations do not truncate. A strict
comparison on the raw direct-sum models would have to absorb
infinitely many nonvanishing higher corrections by a single ordinary
chain-homotopy package. This is what fails. The coderived theorem
survives because every defect is still divisible by the central
curvature.

A spectral replacement remains viable. Let
$K_g = \operatorname{cone}(f_g)$ and filter it by bar degree, total
conformal weight, or, more sharply for class~$\mathsf{M}$, by a
shadow-window filtration in which the quotient by $F^{R+1}$ keeps only
the discrepancy classes of shadow degree at most~$R$. Each finite
window then sees only finitely many nonzero operations, so the
associated-graded comparison becomes a finite problem.
Proposition~\ref{prop:coderived-bar-degree-spectral-sequence}
supplies the corresponding coderived spectral sequence, with strict
$E_1$ page because the curvature lies in positive filtration. The
research target is a spectral form of MC5 whose higher differentials
record the scalar-channel harmonic classes $c_r(\cA)$ and whose abutment is a
coacyclic cone. This replaces a false strict chain identity by a
filtered comparison that measures the class~$\mathsf{M}$ defect page
by page.

The strongest chain-level statement presently visible is completed
rather than strict. Proposition~\ref{prop:standard-strong-filtration}
and Theorem~\ref{thm:completed-bar-cobar-strong} already provide the
weight-completed bar side, and
Corollary~\ref{cor:virasoro-postnikov-nontermination} shows why
class~$\mathsf{M}$ also needs completion in shadow degree. Since the
full Maurer--Cartan class satisfies
$\Theta_\cA = \varprojlim_r \Theta_\cA^{\le r}$ in the completed
convolution algebra, the BV analogue belongs in the same completed
regime. The natural target is a continuous comparison of
bi-completed models
\[
\widehat f_g \colon
\widehat C^{\bullet}_{\mathrm{BV}}(\cA,\Sigma_g)
\longrightarrow
\widehat B^{(g)}(\cA),
\]
where the hats denote inverse limits over finite weight truncations
and finite shadow windows, equivalently a pro-object built from those
finite quotients. The conjectural statement is not that the raw
direct-sum complexes are quasi-isomorphic, but that each finite
quotient of $\widehat f_g$ is a strict quasi-isomorphism and that the
inverse-limit comparison is continuous and filtration-compatible. This
is stronger than Theorem~\ref{thm:bv-bar-coderived-vol1}, because it
remembers every finite stage, and weaker than a raw chain-level
quasi-isomorphism, because it allows the infinite class~$\mathsf{M}$
defect to die only after completion.

Between ordinary chain level and bare coderived equivalence lies an
intermediate strengthening. One may ask that $\widehat f_g$ be a weak
equivalence of filtered curved models in the sense of
Definition~\ref{def:curved-weak-equiv}, equivalently an isomorphism
already in the provisional coderived category of
Definition~\ref{def:provisional-coderived}. This retains the full
filtered-completed class~$\mathsf{M}$ tower while remaining compatible
with the proved coderived theorem. With the available hypotheses, this
filtered-completed spectral statement is the sharpest plausible
upgrade of MC5 for class~$\mathsf{M}$.
\end{remark}

\section{Non-Calabi--Yau local surfaces and the Burns datum}
\label{sec:non-cy-local-surfaces}
\index{Burns space|textbf}
\index{local surface!non-Calabi--Yau}

The holomorphic-topological boundary VOAs of twisted supergravity
on non-Calabi--Yau local surfaces furnish a family of class~$\mathsf{C}$
algebras whose Koszul datum is controlled by a single integer
\textup{(}the rank of the characteristic lattice\textup{)}. The Burns
space is the simplest member.

\begin{computation}[Burns space Koszul datum;
\ClaimStatusProvedElsewhere]
\label{comp:v1-burns-koszul-datum}
\index{Burns space!Koszul datum}
\index{$\beta\gamma$ system!Burns}
The boundary VOA of the Burns space consists of four $\beta\gamma$
pairs with an $SO(8)$ global symmetry, giving:
\begin{itemize}[nosep]
\item central charge $c_{\mathrm{Burns}}
 = 4 \cdot c_{\beta\gamma}(\lambda{=}1)
 = 4 \cdot 2 = 8$,
 using $c_{\beta\gamma}(1) = 2(6 - 6 + 1) = 2$;
\item modular characteristic
 $\kappa_{\mathrm{Burns}} = c_{\mathrm{Burns}}/2 = 4$;
\item shadow class~$\mathsf{C}$ globally \textup{(}shadow depth
 $r_{\max} = 4$, governed by the quartic contact term of the
 $\beta\gamma$ system\textup{)}, degenerating to class~$\mathsf{M}$
 \textup{(}$r_{\max} = \infty$\textup{)} along the $T$-line, where
 the stress tensor becomes a fundamental generator;
\item genus-$1$ obstruction
 $F_1^{\mathrm{Burns}} = \kappa_{\mathrm{Burns}}/24 = 4/24 = 1/6$;
\item genus-$2$ obstruction
 $F_2^{\mathrm{Burns}} = \kappa_{\mathrm{Burns}} \cdot
 \lambda_2^{\mathrm{FP}} = 4 \cdot 7/5760 = 7/1440$.
\end{itemize}
Both $F_1$ and $F_2$ are verified by multi-path computation in
\texttt{compute/lib/burns\_space\_koszul\_datum\_engine.py} and the
associated test file
\texttt{compute/tests/test\_theorem\_burns\_f2\_engine.py}
\textup{(}five paths for $\kappa$, six paths for $F_2$\textup{)}.
\end{computation}

\begin{remark}[Burns shadow class, global vs.\ $T$-line]
\label{rem:burns-shadow-class}
On the generic locus of the Burns parameter space, the only
propagating OPE channel is the $\beta\gamma$ binary OPE with a
simple pole, and the quartic contact term arises from the composite
stress tensor $T = {:}\!\beta\partial\gamma\!{:}$; this is the class
$\mathsf{C}$ mechanism of
Remark~\ref{rem:bv-bar-class-c-proof}. Along the $T$-line, $T$
couples to itself as a fundamental generator, so the shadow depth
jumps from $r_{\max} = 4$ to $r_{\max} = \infty$: the Burns datum
degenerates to class~$\mathsf{M}$. The genus expansion on the
$T$-line no longer closes at the scalar level, and the
multi-weight cross-channel correction $\delta F_g^{\mathrm{cross}}$
becomes nonzero at $g \geq 2$. The values
$F_1 = 1/6$ and $F_2 = 7/1440$ are computed on the class-$\mathsf{C}$
generic locus, not on the $T$-line.
\end{remark}

\begin{table}[htbp]
\caption{Non-Calabi--Yau local surfaces: Koszul datum
$(c, \kappa, \mathrm{class}, F_1, F_2)$. Burns is
\ClaimStatusProvedElsewhere{} \textup{(}verified in the compute
layer\textup{)}; the remaining rows are \ClaimStatusConjectured{}
until their \(c,\kappa,F_1,F_2\) values are computed directly.}
\label{tab:non-cy-local-surfaces}
\begin{center}
\small
\renewcommand{\arraystretch}{1.20}
\begin{tabular}{lccccc}
\toprule
Surface & $c$ & $\kappa$ & Class & $F_1$ & $F_2$ \\
\midrule
Burns space \textup{(}$4\beta\gamma$, $SO(8)$\textup{)}
 & $8$ & $4$ & $\mathsf{C}$
 & $1/6$ & $7/1440$ \\[1pt]
Hirzebruch $\mathbb{F}_n$ \textup{(}conj.\textup{)}
 & $2n$ & $n$ & $\mathsf{C}$
 & $n/24$ & $n \cdot 7/5760$ \\[1pt]
del Pezzo $\mathrm{dP}_k$ \textup{(}$k=0,\ldots,8$; conj.\textup{)}
 & $2(k{+}1)$ & $k{+}1$ & $\mathsf{C}$
 & $(k{+}1)/24$ & $(k{+}1) \cdot 7/5760$ \\[1pt]
Enriques surface \textup{(}conj.\textup{)}
 & $22$ & $11$ & $\mathsf{C}$
 & $11/24$ & $11 \cdot 7/5760$ \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

\begin{conjecture}[Hirzebruch, del Pezzo, and Enriques Koszul data;
\ClaimStatusConjectured]
\label{conj:non-cy-local-surfaces}
\index{Hirzebruch surface!Koszul datum}
\index{del Pezzo surface!Koszul datum}
\index{Enriques surface!Koszul datum}
The boundary VOAs of twisted supergravity on the non-Calabi--Yau
local surfaces listed in Table~\textup{\ref{tab:non-cy-local-surfaces}}
have the Koszul data shown there. Concretely:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item \emph{Hirzebruch $\mathbb{F}_n$:} the characteristic lattice
 $H^{2}(\mathbb{F}_n, \mathbb{Z})$ has rank~$2$, so the boundary
 VOA decomposes into $n$ isomorphic $\beta\gamma$ pairs
 \textup{(}one pair per self-intersection unit along the fibre
 direction\textup{)}, giving
 $\kappa(\mathbb{F}_n) = n$ linearly in the Hirzebruch parameter.
\item \emph{del Pezzo $\mathrm{dP}_k$:} the dimension
 $\dim H^{2}(\mathrm{dP}_k, \mathbb{R}) = k + 1$ controls the
 number of $\beta\gamma$ pairs in the boundary VOA, giving
 $\kappa(\mathrm{dP}_k) = k + 1$. At $k = 0$ \textup{(}$\mathbb{P}^2$,
 $\kappa = 1$\textup{)} and $k = 8$ \textup{(}maximal blow-up,
 $\kappa = 9$\textup{)} the numerics are predicted to match the
 characteristic-lattice dimension prediction.
\item \emph{Enriques surface:} a $\mathbb{Z}/2$ quotient of a K3 surface,
 and the K3 boundary VOA carries $\kappa(\mathrm{K3}) = 24$
 \textup{(}the $24$-dimensional Niemeier lattice\textup{)}. The
 quotient halves the characteristic lattice and loses a single unit
 from the fixed locus contribution, giving
 $\kappa(\mathrm{Enriques}) = 11$ rather than~$12$.
\end{enumerate}
In all three cases, the shadow class is conjectured to be
$\mathsf{C}$ on the generic locus \textup{(}four-pair $\beta\gamma$
structure\textup{)} and to degenerate to $\mathsf{M}$ along the
stress-tensor line, in direct analogy with the Burns space
\textup{(}Remark~\textup{\ref{rem:burns-shadow-class}}\textup{)}.
Direct verification via multi-path computation is open.
\end{conjecture}

\begin{remark}[Scope and status]
\label{rem:non-cy-scope}
The Burns row of Table~\ref{tab:non-cy-local-surfaces} is the only
entry that is presently computed from the engine; it is
\ClaimStatusProvedElsewhere{} by the five-path $\kappa$ verification
and the six-path $F_2$ verification in the compute layer. The
Hirzebruch, del~Pezzo, and Enriques rows are
\ClaimStatusConjectured{} predictions based on dimensional counting
of the characteristic lattice and the general class-$\mathsf{C}$
pattern $F_g = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}$ on the
uniform-weight lane of Theorem~D.
No claim is made that these families are uniformly class~$\mathsf{C}$
on their full parameter spaces: the analogous jump to class
$\mathsf{M}$ along codimension-one loci for non-Calabi--Yau local
surfaces with composite stress tensor is a conjectural pattern, and it
requires a systematic discriminant and shadow-tower computation.
\end{remark}

\section{Affine WZW bar-BRST addendum}

\begin{proposition}[Genus-\texorpdfstring{$0$}{0} WZW BRST complex from the affine bar complex;
\ClaimStatusConditional]
\label{prop:wzw-brst-bar-genus0}
\index{WZW model!BRST complex as bar complex}
\index{BRST!WZW genus-0 bar comparison}
Let $\fg$ be a simple Lie algebra with dual Coxeter number~$h^\vee$,
and let $k \notin \Sigma(\fg) \cup \{-h^\vee\}$ be generic
\textup{(}in particular $k \neq -h^\vee$, so that the Sugawara
construction is well-defined\textup{)}. The affine vertex algebra
$V_k(\fg)$ carries the classical $r$-matrix
\begin{equation}\label{eq:wzw-r-matrix-brst}
r^{\mathrm{KM}}(z) = k\,\Omega/z,
\end{equation}
where $\Omega \in \fg \otimes \fg$ is the Casimir tensor, and the
curvature coefficient
\begin{equation}\label{eq:wzw-kappa-brst}
\kappa\bigl(V_k(\fg)\bigr)
= \frac{\dim(\fg)\,(k + h^\vee)}{2h^\vee}.
\end{equation}
Write
\[
 C_{\mathrm{BRST}}^{\bullet,\mathrm{WZW}}(\fg,k)
 \;:=\;
 \bigl(
 C^{\infty/2+\bullet}(\widehat{\fg}_k, V_k(\fg)),\,
 Q_{\mathrm{BRST}}^{\mathrm{WZW}}
 \bigr)
\]
for the standard semi-infinite BRST complex of the genus-$0$ WZW
model, and write
\[
 \barB^{\mathrm{ch}}_0\bigl(V_k(\fg)\bigr)
 \;=\;
 T^c\bigl(s^{-1}\overline{V_k(\fg)}\bigr),
 \qquad
 \overline{V_k(\fg)} := \ker(\epsilon),
\]
for the genus-$0$ chiral bar complex, with desuspension
$|s^{-1}v| = |v| - 1$. Then for every degree $n \geq 3$
\textup{(}the stability range $2g - 2 + n > 0$ at genus~$0$\textup{)},
the WZW BRST complex is computed by the affine bar complex: there
is a natural filtered quasi-isomorphism
\begin{equation}\label{eq:wzw-brst-bar-qi}
 C_{\mathrm{BRST}}^{\bullet,\mathrm{WZW}}(\fg,k)
 \xrightarrow{\;\sim\;}
 \bigl(
 \barB^{\mathrm{ch}}_0\bigl(V_k(\fg)\bigr),\,
 d_{\mathrm{bar}}
 \bigr).
\end{equation}
On the PBW-associated graded, the BRST differential
$Q_{\mathrm{BRST}}^{\mathrm{WZW}}$ equals the bar differential
$d_{\mathrm{bar}}$; both reduce to the Chevalley--Eilenberg
differential $d_{\mathrm{CE}}$ of the loop algebra subalgebra
$\widehat{\fg}_{k,-} := \fg \otimes t^{-1}\mathbb{C}[t^{-1}]$
acting on the vacuum module~$V_k(\fg)$.
\end{proposition}

\begin{proof}
The argument extends
Theorem~\ref{thm:brst-bar-genus0} \textup{(}the $c = 26$ string
case\textup{)} by replacing the Virasoro BRST complex with the
affine semi-infinite complex, and invokes
Theorem~\ref{thm:bar-semi-infinite-km} for the comparison.

\emph{Step~1: Bar--semi-infinite comparison.}
Theorem~\ref{thm:bar-semi-infinite-km} provides a filtered
quasi-isomorphism between the affine bar complex
$\barB^{\mathrm{ch}}(\widehat{\fg}_k)$ and the semi-infinite complex
$C^{\infty/2+\bullet}(\widehat{\fg}_k, V_k)$ for every
$k \neq -h^\vee$. The semi-infinite complex is the standard
genus-$0$ BRST presentation of the WZW model, so it remains to
identify the differentials on the PBW-associated graded.

\emph{Step~2: PBW filtration and Chevalley--Eilenberg reduction.}
At generic level, Theorem~\ref{thm:km-chiral-koszul} and
Proposition~\ref{prop:km-generic-acyclicity} place $V_k(\fg)$ on the
chirally Koszul locus. On the BRST side, the associated graded
differential is the Chevalley--Eilenberg differential~$d_{\mathrm{CE}}$
of the current Lie algebra $\widehat{\fg}_{k,-}$ acting on the
vacuum module. On the bar side, the associated graded differential
is extracted from the current OPE
$J^a(z) J^b(w) \sim k\,\Omega^{ab}/(z-w)^2 + f^{ab}{}_c J^c(w)/(z-w)$,
which is the same bracket that defines~$d_{\mathrm{CE}}$.
The filtered comparison therefore lifts the Chevalley--Eilenberg
identification to the full genus-$0$ complexes.

\emph{Step~3: Degree propagation.}
Since $V_k(\fg)$ is chirally Koszul at generic level, the bar spectral
sequence collapses on the Koszul line and each finite-length summand of
$T^c(s^{-1}\overline{V_k(\fg)})$ is generated by the binary residue
bracket and its iterates. The genus-$0$ BRST/bar identification
propagates from the binary comparison to every finite degree $n \geq 3$.
\end{proof}

\begin{conjecture}[All-genera WZW BRST/bar identification at generic level;
\ClaimStatusConjectured]
\label{conj:wzw-brst-bar-all-genera}
\index{WZW model!all-genera BRST/bar identification}
Let $\fg$ be simple and let
$k \notin \Sigma(\fg) \cup \{-h^\vee\}$ be generic. For every
genus $g \geq 0$ and every degree $n \geq 1$, the renormalized
BV-BRST complex of the genus-$g$ WZW model with $n$ marked points is
filtered quasi-isomorphic to the genus-$g$, degree-$n$ bar complex of
$V_k(\fg)$. At $g=0$ this is
Proposition~\ref{prop:wzw-brst-bar-genus0}; the remaining content is
the higher-genus MC5 comparison between the handle-gluing BRST
operator and the modular bar differential.
\end{conjecture}

\begin{remark}[Generic level, critical level, and the free-string limit]
\label{rem:wzw-brst-bar-generic-level}
The generic-level hypothesis is used twice. First, the proof of
Proposition~\ref{prop:wzw-brst-bar-genus0} uses the chirally Koszul
package of Theorem~\ref{thm:km-chiral-koszul} and
Proposition~\ref{prop:km-generic-acyclicity} to force the PBW
spectral sequence onto its Chevalley--Eilenberg line. Second, the
generic affine center is the small one used by the filtration
argument. At the critical level $k=-h^\vee$, the scalar class
$\kappa(V_k(\fg))$ vanishes, the Sugawara grading used in the generic
argument is replaced by the separate critical package, and the
Feigin--Frenkel center jumps
\textup{(}Theorem~\ref{thm:critical-level-structure}\textup{)}.
The proposition is therefore stated only on the generic lane.

The affine gauge ghosts contribute one fermionic $bc$ pair for each
basis vector of~$\fg$, hence
\[
 c_{\mathrm{ghost}}^{\mathrm{WZW}} = -2\dim(\fg).
\]
This is the same numerical contribution carried by the odd
Koszul-dual generators in the Chevalley--Eilenberg bar model.

For $\fg = \mathfrak{u}(1)$, the matter algebra is Heisenberg, so the
genus-$0$ comparison reduces to the abelian bar/BRST identification
already used in Theorem~\ref{thm:brst-bar-genus0}. Taking $26$
copies recovers the free matter sector $\mathcal{H}^{26}$ of the
bosonic string. Coupling that abelian matter to the reparametrizing
$bc$ ghosts gives the MC5 genus-$0$ case proved in
Theorem~\ref{thm:brst-bar-genus0} and
Corollary~\ref{cor:anomaly-physical-genus0-vol1}. The affine ghost count
$c_{\mathrm{ghost}}^{\mathrm{WZW}} = -2\dim(\fg)$ belongs to the WZW
gauge-theory sector; the string-theoretic ghost count
$c_{bc} = -26$ is a separate reparametrization contribution.
\end{remark}

\section{BV-BRST and the K3 1-loop anomaly}
\label{sec:bvbrst-supplement}

\begin{remark}[6d holomorphic Chern--Simons quartic anomaly polynomial;
\ClaimStatusProvedElsewhere]
\label{rem:bvbrst-6d-hcs-quartic}
\index{6d holomorphic Chern--Simons!quartic anomaly|textbf}
\index{anomaly polynomial!quartic adjoint Casimir}
\emph{Type signature.} (CY quadrant via Vol~III; chain-level
presentation; Beilinson level $0$ on the factorisation dg-cat;
hypothesis package: CY$_3$ trivialisation $\omega_X\cong\mathcal O_X$,
quartic adjoint Casimir, formal locus + global descent.)

The Costello $5$-brane vertex algebra~\cite{Costello2021hCS} sits
inside $6$d holomorphic Chern--Simons on a Calabi--Yau threefold,
whose $1$-loop BV obstruction is governed by the \emph{quartic} adjoint
Casimir
$\mathrm{tr}_{\mathrm{adj}}\bigl(T^{(a}T^bT^cT^{d)}\bigr)_{\mathrm{sym}}$
through the anomaly polynomial
\[
 \mathrm{Anom}^{6\mathrm{d\,hCS}}_{1\text{-loop}}(X)
 \;=\; \int_X \Tr_{\mathrm{ad}}\bigl(A\,(F_A)^3\bigr),
\]
of degree $4$ in the gauge field $A$. The canonical ghost-side
representative is the descended cocycle
$c\wedge(\bar\partial c)^{\wedge 4}/(2\pi i)^3$ of ghost number~$1$ and
form degree $0+4$; CS descent
$F=\bar\partial c+\tfrac12[c,c]$ converts it to the $A$-side bubble
above. The $5$d analogue (Costello--Yagi) carries the cubic Casimir
$d^{abc}_\fg=\mathrm{tr}_{\mathrm{ad}}(\{T^a,T^b\}T^c)$, which vanishes
on every simple $\fg$ outside $A_n$ ($n\geq 2$); the $6$d quartic
Casimir is non-vanishing on every simple $\fg$ and is the genuine
load-bearing obstruction. The dimensional shift from $5$d to $6$d
raises the anomaly degree by one: $3$d Chern--Simons carries the cubic
$\int\Tr(A\wedge dA + \tfrac23 A\wedge A\wedge A)$ classical action,
not the quartic $1$-loop anomaly polynomial. Primary verification:
Costello--Li twisted-supergravity quantisation~\cite{CL16},
Costello--Li anomaly cancellation~\cite{CL20}, Costello $5$-brane
vertex algebra~\cite{Costello2021hCS}.

The cross-volume placement is Vol~III at level~$0$ of the Beilinson
tower: the factorisation dg-cat $\mathcal C^{\mathrm{op}}$ on
$(X, D, \tau)$ is holographically identified with the CY-cat via
$6$d hCS through the formal-locus to global-descent reconstruction
theorem with hypothesis package (matched-conventions target datum,
QME, locality, anomaly cancellation). The two-stage CY-to-chiral
functor $\Phi_3^{(\Sigma_2, C)}=\mathrm{Sp}^{\mathrm{ch}}_{\Sigma_2,C}
\circ\Phi_3^{\mathrm{FA}}$ at $d=3$ takes the level-$0$ datum to level
$2$ with specialisation data $(\Sigma_2, C)=(K3\text{-fibre slice},$
divisor curve in the Mukai lattice$)$ named explicitly.

\emph{Three independent verification paths for the
quartic-not-cubic identification.}
\textup{(a)} \emph{Form-degree balance.} On a CY$_3$ with
$\Omega_X\in\Omega^{3,0}(X)$, the gauge field $A\in\Omega^{0,1}(X,\fg)$
and curvature $F_A\in\Omega^{0,2}(X,\fg)$; the integrand
$\Omega_X\wedge\Tr_{\mathrm{ad}}(A\,F_A^{\,3})$ has Dolbeault type
$(3, 1+2+2+2)=(3,7)$ which integrates against the volume form on the
real 6-fold $X$ after one antiholomorphic delta-localisation, while
the cubic candidate $\Omega_X\wedge\Tr(A\,F_A^{\,2})$ of type $(3,5)$
fails the $\bar\partial$-cocycle condition by an even shift; the
parity matches the four-vertex one-loop wheel and forbids three.
\textup{(b)} \emph{Ghost-side BRST descent.} The descent equation
$d_{\mathrm{BRST}}\omega^{(p,q)}=d\omega^{(p+1,q-1)}$ takes the
level-zero anomaly cocycle $c\wedge(\bar\partial c)^{\wedge 4}$ to the
$A$-side via $F=\bar\partial c+\tfrac12[c,c]$; the resulting $A$-side
representative is degree~$4$ in $A$, and the rank-$4$ adjoint Casimir
is the only $\mathrm{ad}$-invariant of the matching tensor type.
\textup{(c)} \emph{Lower-dimensional contrast.}
$5$d~hCS on $\R\times\C^2$ with simply-laced bosonic $\fg$
(Costello~$2021$~\cite{Costello2111} on the M-theory $\Omega$-background
$5$d non-commutative gauge theory, in the Costello--Witten--Yamazaki
gauge-theory-and-integrability frame~\cite{CWY18}) has vanishing
one-loop anomaly because the rank-$3$ Casimir
$d^{abc}_\fg=0$ on ADE; in $6$d the corresponding rank-$4$ tensor
$\mathrm{tr}_{\mathrm{ad}}(T^{(a}T^bT^cT^{d)})$ is non-vanishing on
\emph{every} simple $\fg$, distinguishing the dimensional shift and
ruling out cubic-Casimir reduction (Costello--Li~\cite{CL20}).
\end{remark}

\begin{remark}[Paramodular anomaly cancellation as Deligne cohomology obstruction;
\ClaimStatusHeuristic]
\label{rem:bvbrst-paramodular-anomaly}
The BV-BRST anomaly-cancellation framework of Vol~I specialises at $K3 \times T^2$ to a
Deligne cohomology class in $H^2(\overline{\mathcal{A}_2}, \mathcal{O}^*)$; in the
heuristic twisted-supergravity comparison the distinguished trivialiser
is the Gritsenko--Nikulin Igusa cusp form $\Delta_5$
of weight $5$ for $K3 \times T^2$ Omega-deformed with $24$
M5-branes wrapping the $I_1$ Kodaira fibres. The arithmetic constant is the
Borcherds denominator weight
\[
 \kappa_{\mathrm{BKM}}(\Delta_5)=\frac{c_1(0)}{2}=5
\]
in the Gritsenko--Nikulin normalisation; it is neither a chiral
conductor nor obtained in this volume by an additive identity
$5=\chi(\mathcal O_{K3})+\sum_{24}\mathrm{Res}(I_1)$. The residue
description is a physical normalisation frame for the same divisor
class. Four duality frames (heterotic Harvey--Moore $1996$; IIB D1-D5
DVV $1996$--$1997$; IIA DMVV $1997$; M-theory Witten $1995$) all
produce the same form. The physics input is Costello's $5$-brane
vertex algebra~\cite{Costello2021hCS} (sitting inside $6$d
holomorphic Chern--Simons with quartic anomaly polynomial
$\int_X\Tr_{\mathrm{ad}}(A\,(F_A)^3)$,
Remark~\ref{rem:bvbrst-6d-hcs-quartic}) and Costello--Gaiotto twisted
M-theory~\cite{CostelloGaiotto2018}; the Deligne-class comparison is
used here as a heuristic bridge to the level-$0$ holographic
equivalence with Vol~III's CY-cat under the two-stage functor
$\Phi_3^{(\Sigma_2, C)}$, not as a proved theorem of this volume.
\end{remark}

\begin{remark}[K3 conductor carriers: ghost, Mukai, and Borcherds;
\ClaimStatusHeuristic]
\label{rem:bvbrst-koszul-conductor}
The K3 lane contains three conductors with different carriers. The
BRST ghost-resolution conductor is
$K_{\mathrm{univ}}^{\mathrm{BRST}}(A)
=-\tfrac12c_{\mathrm{ghost}}(\BRST(A))$ after choosing a ghost system.
The Mukai-enhanced Theorem~C conductor is
\[
 K^{\kappa_{\mathrm{ch}}}(\mathcal{H}_{\mathrm{Muk}})
 =2c_+(\mathrm{Mukai}(K3))=8,
\]
the $\mathcal B$-family value that extends the Theorem~C scalar set to
$\{0,8,13,250/3,98/3\}$. The Borcherds denominator conductor is instead
\[
 \kappa_{\mathrm{BKM}}(\mathfrak g_{\Delta_5})=c_1(0)/2=5.
\]
Bruinier's Heegner--Chern reciprocity supplies the automorphic divisor
target~\cite[Proposition 5.1]{Bruinier2002}; it does not by itself
identify the Mukai value $8$ with the Borcherds weight $5$. The
specialisation $\hbar_{\mathrm{qg}}^2K^{\kappa_{\mathrm{ch}}}=-1$ and
the Lusztig order $\ell=8$ require the separate monodromy, PBW
truncation, parity, and bulk-boundary comparison data recorded in the
K3 concordance. They are comparison targets, not Vol~I scalar
identities.
\end{remark}

\section{2-loop obstruction vanishing
on the K3-twisted-holography line}
\label{sec:bvbrst-supplement-ii}

The $1$-loop origin of $\Delta_5$ is the classical / $\hbar^1$ BV
master-equation datum
$\tfrac{1}{2}\{S_{\mathrm{cl}} + \hbar S^{(1)},
S_{\mathrm{cl}} + \hbar S^{(1)}\}_{\mathrm{BV}}
+ \hbar\,\Delta_{\mathrm{BV}}(S_{\mathrm{cl}} + \hbar S^{(1)})
= O(\hbar^2)$
on twisted $11$D supergravity on $\bR^3\times K3\times\bC^2$ with $24$
M$5$-branes wrapping Kodaira $I_1$ fibres of the elliptic K3
\cite{Costello2016renormalization,Costello2013holography,CostelloGaiotto2018,Costello2021hCS}.
The next order is the $\hbar^2$ piece of the quantum master equation.
The statement needed in this volume is a conditional comparison:
if the local BV obstruction complex, the renormalised two-loop graph
functional, and the Siegel--Borcherds normalisation are identified in
the specified K3 background, then the two-loop class is exact.

\begin{proposition}[Conditional two-loop BV obstruction cancellation;
\ClaimStatusConditional]
\label{prop:bvbrst-2loop-obstruction}
\index{BV quantisation!2-loop obstruction|textbf}
\index{K3 twisted holography!2-loop|textbf}
Let $S_q = S_{\mathrm{cl}} + \hbar\,S^{(1)} + \hbar^2\,S^{(2)} + O(\hbar^3)$
be the quantum BV action of twisted $11$D supergravity on
$\bR^3\times K3\times\bC^2$ with $24$ M$5$-branes on the Kodaira $I_1$
fibres (the twisted-$11$D-SUGRA datum). Write the gauge algebra
$\mathfrak{m}_{K3} := \mathfrak{g}_{\Delta_5}|_{\text{gauge sector}}$.
Assume:
\begin{enumerate}[label=\textup{(\alph*)}]
\item the Costello local-functional obstruction complex for this
background is identified with the invariant line
$\bC\cdot[\Delta_5]\subset H^2(\mathfrak m_{K3},\bC)$;
\item the chosen renormalisation scheme evaluates the two-loop graph
sum on the K3 background as
$I_\Theta+I_D+I_\infty=0$;
\item the Siegel--Borcherds normalisation sends this line to the
$p^2$ coefficient of
$\log(\Phi_{10}^{\mathrm{un}}/\eta^{24})$ after removing the
one-loop Weyl and $\eta^{24}$ factors.
\end{enumerate}
Then the $2$-loop obstruction class
\[
 \mathrm{obs}^{(2)} \;=\; \{S_{\mathrm{cl}}, S^{(2)}\}_{\mathrm{BV}}
 + \tfrac{1}{2}\{S^{(1)}, S^{(1)}\}_{\mathrm{BV}}
 + \Delta_{\mathrm{BV}} S^{(1)}
 \;\in\; H^1(C^{\mathrm{BV}}_\bullet,\,\bC)
\]
maps to $c_2\cdot[\Delta_5]$ with
\[
 c_2 \;=\; 0.
\]
Consequently there exists $S^{(2)}$ satisfying the $\hbar^2$ quantum
master equation modulo BV-exact terms in this comparison frame.
\end{proposition}

\begin{proof}
Assumption~(a) places the obstruction in the single invariant line
$\bC\cdot[\Delta_5]$, so
$\mathrm{obs}^{(2)}=c_2[\Delta_5]$ after applying the comparison map.
Assumption~(b) evaluates the local graph representative of the same
class as zero. Assumption~(c) fixes the normalisation of this zero
against the $p^2$ Fourier--Jacobi coefficient, so no hidden Weyl-vector
or $\eta^{24}$ term remains. Hence $c_2=0$, and the order-$\hbar^2$
quantum master equation can be solved after adding a BV-exact
counterterm.
\end{proof}

\begin{remark}[Theta-graph normalisation at $\chi(K3)=24$]
\label{rem:bvbrst-theta-graph}
The graph-level assumption in
Proposition~\ref{prop:bvbrst-2loop-obstruction} uses the following
normalisation target. With the Costello propagator and the K3 Kähler
normalisation fixed, the theta-graph $2$-loop Feynman integral should
contribute
\[
 I_\Theta \;=\; \frac{1}{2}\int_{K3} c_2(K3)\wedge\omega
 \;=\; \tfrac{1}{2}\chi(K3)\cdot [\omega]
 \;=\; 12\cdot[\omega]
\]
by the Chern--Gauss--Bonnet evaluation of $c_2(K3)$ against the Kähler
class $\omega$ \cite{BeauvilleK3,BPVdV2004K3surfaces}. The remaining
local calculation is the equality
\[
 I_\Theta + I_D + I_\infty
 \;=\; 12 + 2\cdot 12\cdot(\text{res coefficient}) - 24\cdot(\text{res coefficient}) \;=\; 0,
\]
in the same renormalisation scheme. This is not a second derivation of
the Borcherds weight $5$; it is the graph-side open mathematical condition for the
conditional two-loop cancellation.
\end{remark}

\begin{remark}[BV obstruction versus anomaly cancellation scope]
\label{rem:bvbrst-scope}
Proposition~\ref{prop:bvbrst-2loop-obstruction} is a conditional statement
about the $\hbar^2$ quantum master equation on the specific field
configuration of twisted-$11$D-SUGRA on $\bR^3\times K3\times\bC^2$
with $24$ M$5$-branes wrapping Kodaira $I_1$ fibres of the elliptic
K3, Omega-deformed in the $\bC^2$ transverse factor. The conditional
vanishing $c_2 = 0$ is \emph{specific} to this background; at
$\hbar^3$ the expected identification of the Igusa form as the
classification invariant in $H^2(\mathfrak{m}_{K3})$ allows a
non-trivial obstruction proportional to $[\Delta_5]^2 = [\Delta_{10}]$,
predicted to be non-zero (the pentagon $\hbar^3$ failure needing the
$\Phi_{10}/\eta^{24}$ associator twist). A proof of the comparison
hypotheses would verify obstruction-free BV quantisation through two
loops and pin the first non-trivial obstruction to $\hbar^3$.
\end{remark}

\begin{remark}[Two $\hbar$'s: loop-counting $\hbar$ versus
specialisation $\hbar^2 = -1/8$]
\label{rem:bvbrst-two-hbar}
The K3-twisted-holography construction contains two distinct
$\hbar$ parameters. The parameter $\hbar_{\mathrm{BV}}$ is the
loop-counting parameter of the BV quantisation above, formal in
power series $\bC[\![\hbar_{\mathrm{BV}}]\!]$; $\hbar^2_{\mathrm{qg}}
= -1/8$ is the Lusztig specialisation of the Hall--Drinfeld double
$\mathcal{D}_\hbar(\mathrm{CoHA}_{K3\times E})$ at $\zeta^8 = 1$
(Bruinier $2002$ Proposition~$5.1$). The
bridge is this: $\hbar_{\mathrm{BV}}$ parametrises the formal deformation of
the classical BV action; $\hbar_{\mathrm{qg}}$ parametrises the
roots-of-unity limit of the associated quantum group. They coincide
only on the formal side (they are equated as formal parameters
within the holography line); the numerical specialisation
$\hbar^2_{\mathrm{qg}} = -1/8$ takes a definite value of
$\hbar_{\mathrm{BV}}$ only after passage to the root-of-unity phase.
\end{remark}

\begin{remark}[Partition function match to $\log\Phi_{10}$]
\label{rem:bvbrst-partition-match}
The conditional $2$-loop comparison in
Proposition~\ref{prop:bvbrst-2loop-obstruction} requires matching the
BV partition function on $T^2\times K3$ with the $p^2$ Fourier
coefficient of $\log\Phi_{10}(Z)$ after Wick rotation to Euclidean
signature and Siegel-to-paramodular reduction. In that normalisation,
the $p^2$ Fourier coefficient of $\log\Phi_{10}$ is
$(-24\log\eta)|_{p^0} + 2c(\phi_{10,1})|_{p^1} + O(p^3)$ with
$c(\phi_{10,1}) = 0$ at the first Jacobi-index level (Gritsenko 1999,
$\eta^{24}/\phi_{10,1}$), so the $p^2$ coefficient reduces to $-24$
times the standard Eisenstein-$E_2^*$ completion term. The graph-side
open mathematical condition of Remark~\ref{rem:bvbrst-theta-graph} is to produce
this prefactor in the same scheme; the completion term is then absorbed
by the Omega-background modification. Cross-volume check: Vol~III
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic} establishes the same
$\Phi_{10}$ partition function from the Hall-Drinfeld-double side,
independently reproducing this coefficient.
\end{remark}

\section{chain-level $\mu_8$-gerbe banding
cocycle as BV counterterm}
\label{sec:bvbrst-supplement-iii}

At the $(\infty,1)$-level, the associator
$\widetilde{\Phi}^{\mathrm{Sieg\text{-}Bor}}_{\mathrm{Sp}_4}[\Phi_{10}/\eta^{24}]$
is conjectured to define a $\mu_8$-gerbe $\mathcal{G}$ on
$\overline{\mathcal{A}_2}$. The carrier is the Heegner--Chern torsion
lane, not the BV graph lane. The statements below spell out the exact
cocycle and counterterm hypotheses needed to trivialise the gerbe on
$U := \overline{\mathcal{A}_2}\setminus(H_1\cup H_4)$ and compare that
trivialisation with the root-of-unity phase
$\hbar_{\mathrm{qg}}^2 = -1/8$.

\begin{proposition}[Conditional \v Cech $2$-cocycle for the $\mu_8$-gerbe;
\ClaimStatusConditional]
\label{prop:bvbrst-cech-cocycle}
\index{gerbe!chain-level banding|textbf}
\index{Bruinier!order-8 Heegner-Chern torsion}
\index{Baily-Borel cover!Cech cocycle}
Let $\{U_i\}_{i\in I}$ be the finite open cover of
$U := \overline{\mathcal{A}_2}\setminus(H_1\cup H_4)$ obtained from the
Baily--Borel compactification by deleting $H_1 \cup H_4$ and restricting
the canonical affine cover coming from the Siegel upper half-space
$\mathfrak{H}_2 / \mathrm{Sp}_4(\mathbb Z)$ \textup{(}Faltings--Chai $1990$
\textup{IV}.$6$; Baily--Borel $1966$\textup{).} Let
$\gamma_{ij} \in \mathrm{Sp}_4(\mathbb Z)$ be the transition
modular-group elements witnessing $U_i \cap U_j$. Assume that the
Bruinier Heegner--Chern class has been lifted to an
$\mathrm{Sp}_4(\mathbb Z)$ cocycle
\[
 \mathrm{HeegChern}\colon \mathrm{Sp}_4(\mathbb Z)\to
 \mathrm{Pic}(\overline{\mathcal{A}_2})\otimes\mathbb Z/8
\]
and that its restriction to
$U=\overline{\mathcal A_2}\setminus(H_1\cup H_4)$ has vanishing
Bockstein obstruction. Then the $\mu_8$-gerbe banding
$F_U \in H^2(U,\mu_8)$ admits the \v Cech representative
$F_{ijk}\colon U_{ijk}\to\mu_8$ given by
\[
 F_{ijk} \;=\; \exp\!\bigl(2\pi i\,k_{ijk}/8\bigr),
 \qquad k_{ijk} \;=\; \bigl\langle \mathrm{HeegChern}(\gamma_{jk}),
 [H_1] + [H_4] \bigr\rangle \bmod 8,
\]
where $[H_1]$ and $[H_4]$ are the Humbert divisor classes of
discriminant $1$ and $4$, and the pairing is taken in
$\mathrm{Pic}(\overline{\mathcal{A}_2})\otimes \mathbb Z/8$. The cochain
$F_{ijk}$ is a genuine $2$-cocycle
\[
 F_{jkl}^{\mathrm{W}18}\cdot (F_{ikl}^{\mathrm{W}18})^{-1}\cdot
 F_{ijl}^{\mathrm{W}18}\cdot (F_{ijk})^{-1} \;=\; 1
\]
on every fourfold intersection $U_{ijkl}$, and its class in
$H^2(U,\mu_8)$ is zero; the cocycle is a nontrivial $2$-coboundary
witness to the restricted gerbe trivialisation.
\end{proposition}

\begin{proof}
The assumed Heegner--Chern cocycle is additive with values in
$\mathrm{Pic}(\overline{\mathcal{A}_2})\otimes\mathbb Z/8$. Restriction
to $U$ removes $H_1$ and $H_4$ as divisors, leaving their classes as
cohomology witnesses. The pairing
$\langle \mathrm{HeegChern}(\gamma_{jk}),[H_1]+[H_4]\rangle\bmod 8$
lands in $\mathbb Z/8$ and the exponential lift gives an element of
$\mu_8\subset\bC^*$. Cocycle closure
\[
 \delta k_{ijkl} \;=\; k_{jkl} - k_{ikl} + k_{ijl} - k_{ijk} \;=\; 0 \bmod 8
\]
on $U_{ijkl}$ follows because $\mathrm{HeegChern}\circ\gamma$
satisfies the $1$-cocycle condition in the symplectic group
$\mathrm{Sp}_4(\mathbb Z)$ \textup{(}Kudla--Millson $1990$
Theorem~$3.1$\textup{),} and the pairing with the fixed Humbert class
inherits closure. The final assertion is exactly the assumed Bockstein
vanishing on $U$: after removing $H_1\cup H_4$, the banding class lifts
from $H^2(U,\mu_8)$ to the specified $\mathbb Z/8$ cochain and is
therefore a coboundary.
\end{proof}

\begin{proposition}[Conditional banding as BV zero-loop counterterm;
\ClaimStatusConditional]
\label{prop:bvbrst-banding-counterterm}
\index{BV counterterm!zero-loop banding|textbf}
\index{twisted 11D SUGRA!mu_8 counterterm}
Assume the \v Cech $2$-cocycle $F_{ijk}$ of
Proposition~\textup{\ref{prop:bvbrst-cech-cocycle}} corresponds
under the Kuga--Satake pullback and the Freed--Quinn banding action to
a \emph{zero-loop} BV counterterm in the twisted $11$D SUGRA quantum
action $S_q$. Then the counterterm has the form
\[
 S^{\mathrm{banding}}_{\mathrm{c.t.}} \;=\;
 \frac{2\pi i}{8}\,\int_{U\text{-band}}
 \log F_U \wedge \omega_{K3},
\]
where the integration is over a $U$-banded region of
$\overline{\mathcal{A}_2}\setminus(H_1\cup H_4)$ and $\omega_{K3}$ is
the holomorphic $2$-form on $K3$ pulled back to the $\overline{\mathcal{A}_2}$
moduli via the Kuga--Satake construction. Adding
$S^{\mathrm{banding}}_{\mathrm{c.t.}}$ to $S_{\mathrm{cl}}$
perturbatively trivialises the $\mu_8$-gerbe obstruction at the
zero-loop sector without modifying the one-loop weight-$5$ Igusa-form
anomaly. Its relation to the two-loop obstruction is only through the
separate comparison hypotheses of
Proposition~\ref{prop:bvbrst-2loop-obstruction}.
\end{proposition}

\begin{proof}[Proof sketch]
The Freed--Quinn banding action for a gerbe $\mathcal{G}$ with \v Cech
representative $F_{ijk} \in \mu_8$ is the classical CS-type action
$S_{\mathrm{FQ}} = (2\pi i/N)\int\log F$ with $N = 8$; here we use
$\log\colon\mu_8\to\mathbb Z/8$ extended by the free-part factor to
$\mathbb Q/\mathbb Z$. Under the Kuga--Satake embedding
$\mathcal{A}^{K3}_{\mathrm{Hodge}}\hookrightarrow
\overline{\mathcal{A}_2}$ of
Remark~\ref{V3-rem:cy2ch-phi-K3-comparison} \textup{(}Vol~III
\texttt{cy\_to\_chiral.tex}\textup{),} the cover $\{U_i\}$ of $U$ pulls
back to a cover of the K3-period moduli; the holomorphic $2$-form
$\omega_{K3}$ lifts to a global section via Hodge-type degeneration on
$U$. Adding $S^{\mathrm{banding}}_{\mathrm{c.t.}}$ to $S_q$ shifts the
BV partition function by a $\mu_8$-phase that cancels the
Heegner-Chern order-$8$ torsion on $U$ without affecting higher-loop
data: the derivative $\partial_\hbar$ sees only $\hbar^0$-order terms.
The numerical relation $\chi(K3)=24=3\cdot 8$ is a compatibility check
for the phase convention; it is not a proof that the two-loop graph
sum factors through the banding cocycle.
\end{proof}

\begin{remark}[Heegner-simplex linking-number formula]
\label{rem:bvbrst-linking-number}
\index{Heegner simplex!linking number}
\index{Borcherds!denominator formula}
The Gritsenko--Nikulin denominator $\Phi_{10}/\eta^{24}$ extends to a
Heegner divisor class on $\overline{\mathcal{A}_2}$ whose $\mu_8$-torsion
part is conjectured to be the gerbe banding obstruction
\cite[\S10]{Borcherds1998}. Under the cocycle hypothesis of
Proposition~\ref{prop:bvbrst-cech-cocycle}, an alternative chain-level
representative of $F_U$ is the linking-number formula
\[
 F_U(x_0, x_1, x_2) \;=\;
 \exp\!\bigl(2\pi i/8 \cdot \mathrm{lk}(\mathrm{HS}(x_0, x_1, x_2),\,
 H_1 \cup H_4)\bigr),
\]
where $x_0, x_1, x_2 \in U$ and $\mathrm{HS}(x_0, x_1, x_2)$ is the
Heegner simplex, the $2$-simplex in $\overline{\mathcal{A}_2}$ with
vertices $x_0, x_1, x_2$ bounded by the Heegner-geodesic triangles
joining the three points. The linking number
\[
 \mathrm{lk}(\mathrm{HS},\,H_1\cup H_4) \;=\;
 \#(\mathrm{HS}\cap H_1) + \#(\mathrm{HS}\cap H_4) \bmod 8
\]
counts transverse intersection points of the Heegner simplex with
$H_1\cup H_4$, weighted with sign and reduced modulo $8$. Equivalence
with the \v Cech form of
Proposition~\ref{prop:bvbrst-cech-cocycle} is the required
chain-level open mathematical condition: on the nerve of the
cover $\{U_i\}$ with $x_\alpha \in U_{i_\alpha}$, the Heegner simplex
degenerates to the $2$-simplex $\{i_0, i_1, i_2\}$ in the nerve, and
the linking number recovers $k_{i_0 i_1 i_2}$ by Bruinier--Borcherds
reciprocity~\cite[Theorem 5.2]{Bruinier2002}. Borcherds
\cite[\S10]{Borcherds1998} gives the denominator identities for
reflection BKMs; Bruinier~\cite[Proposition 5.1]{Bruinier2002} gives
the Heegner--Chern divisor formalism. Under the comparison hypothesis,
the linking-number formula connects to Vol~II
Chapter~\ref{ch:hcs-yangian-etale} and Vol~III
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic} where the same
intersection data appears as the $\hbar^3$ Bruinier-reduced Feynman
denominator
$c_3^{\mathrm{Br}}=c_{\phi_{-2,1}}(3)[H_3]=-8[H_3]$.
\end{remark}

\begin{remark}[Two-$\hbar$ bridge: $\hbar_{\mathrm{qg}}^2 = -1/8$
from banding]
\label{rem:bvbrst-two-hbar-banding}
\index{two-hbar bridge!chain-level}
Remark~\ref{rem:bvbrst-two-hbar} pins
$\hbar_{\mathrm{qg}}^2 = -1/8$ at the root-of-unity phase. The
conditional banding construction explains how a denominator-$8$ phase
could be carried by the Heegner--Chern gerbe. The banding counterterm
$S^{\mathrm{banding}}_{\mathrm{c.t.}}$ is the zero-loop input that
would close the Lusztig specialisation loop if the cocycle and
bulk-boundary comparison hypotheses are supplied. Without those
hypotheses, the residual phase obstruction on $H_1\cup H_4$ remains an
open open mathematical condition.
\end{remark}

\begin{remark}[Conditional metaplectic refinement to $\mu_{16}$-gerbe on
$\overline{\mathcal A_2}\setminus H_1$]
\label{rem:bvbrst-mu16-metaplectic-refinement}
\index{gerbe!mu_16@$\mu_{16}$ metaplectic refinement}
\index{Humbert divisor!$H_4$ order-16 torsion}
Assume the $\mu_8$-cocycle $F_{ijk}$ of
Proposition~\ref{prop:bvbrst-cech-cocycle} trivialises the gerbe on
$U = \overline{\mathcal A_2}\setminus(H_1\cup H_4)$. A metaplectic
refinement at $H_4$ would have order $16$, not $8$, if
$\mathrm{ord}_{H_4}(\Phi_{10}) = 2$ (Igusa 1962 \S7 Cor.~2) combines
with the Kuga--Satake metaplectic factor-of-two (Morrison 1984
\emph{Invent.}~75 Thm.~3). Passing to the metaplectic double cover
$\widetilde{\mathrm{Sp}}_4(\mathbb Z)$ and replacing $\Phi_{10}$ by its
paramodular square root $\Delta_5 = \sqrt{\Phi_{10}}$
(Gritsenko 1995 \S3 Thm.~3.2) would produce the refined cocycle
$G_{ij}(Z) = [\Delta_5/\eta^{12}]^{1/8}|_{\widetilde U_i}/
[\Delta_5/\eta^{12}]^{1/8}|_{\widetilde U_j} \in \mu_{16}$ on
$V = \overline{\mathcal A_2}\setminus H_1$, with
$G_{ij}|_U^2 = F_{ij}$. The Vol~III inscription is
Theorem~\ref{V3-thm:modtr-mu16-metaplectic-banding-cocycle} of
\texttt{modular\_trace.tex}. The BV counterterm
$S^{\mathrm{banding}}_{\mathrm{c.t.}}$ of
Proposition~\ref{prop:bvbrst-banding-counterterm} would lift to the
Mp cover as a $\mu_{16}$-valued counterterm
$\widetilde S^{\mathrm{banding}}_{\mathrm{c.t.}}
= (2\pi i/16)\int_{\widetilde V\text{-band}}\log G_V \wedge
\omega_{K3}$, whose descent to $V$ adds a metaplectic sheet-transition
phase $\zeta_{16}^3$ at $H_4$. The Lusztig specialisation
$\zeta^8 = 1$ and the two-$\hbar$ identity
$\hbar_{\mathrm{qg}}^2 = -1/8$ are unchanged: the metaplectic
factor-of-two is orthogonal to the Drinfeld-$\hbar$/BV-$\hbar$ direction.
\end{remark}

\section{All-order BV obstruction as Heegner--Chern coefficients of a
weak Jacobi form}
\label{sec:bvbrst-heegner-all-order}

The preceding analysis isolates the order-by-order pattern expected for
the BV obstruction cohomology classes
$c_n \in H^2(\mathfrak{g}_{\Delta_5}, \bC)\cong \bC\cdot[\Delta_5]$ on
twisted $11$D~SUGRA on $\bR^3\times K3\times\bC^2$ with $24$~M$5$-branes
on the Kodaira~$I_1$ fibres of the elliptic~K3: $c_1$ fixed
via the one-loop paramodular anomaly, $c_2 = 0$ after the comparison
hypotheses of Proposition~\ref{prop:bvbrst-2loop-obstruction}, and the
three-loop Bruinier-reduced class
\[
 c_3^{\mathrm{Br}}
 =
 c_{\phi_{-2,1}}(3)[H_3]
 =
 -8[H_3]
\]
computed from the discriminant-$3$ coefficient of $\phi_{-2,1}$
\textup{(}Proposition~\ref{prop:bvbrst-2loop-obstruction}; companion
Vol~II three-loop obstruction theorem\textup{).} The scalar
$176256=p_{24}(5)=\chi(\operatorname{Hilb}^5(K3))$ is the fifth
K3 Fock/Hilbert-sector dimension, not a BV obstruction coefficient.
The natural continuation to all orders $n\geq 1$ is the content of the
present section.

\begin{theorem}[Conditional Heegner pattern for the all-order BV obstruction
tower; \ClaimStatusConditional]
\label{thm:bvbrst-heegner-all-order}
\index{BV obstruction!all-order Heegner pattern|textbf}
\index{weak Jacobi form!\phi_{-2,1}@$\phi_{-2,1}$ and BV obstruction}
\index{Bruinier!Heegner-Chern reciprocity all-order}
Let $S_q = S_{\mathrm{cl}} + \sum_{n\geq 1}\hbar_{\mathrm{BV}}^n S^{(n)}$ be the BV
quantum action of twisted $11$D~SUGRA on
$\bR^3\times K3\times\bC^2$ with $24$~M$5$-branes on the Kodaira~$I_1$
fibres of the elliptic~K3, in the Costello--Li holomorphic-topological
twist \cite{Costello2015omega,CostelloLi2016} and the
Costello--Gaiotto--Paquette tree-level holography
frame~\cite{CostelloGaiottoPaquette2018}. For each $n\geq 1$, let
\[
 c_n \;:=\; \bigl[\{S_{\mathrm{cl}}, S^{(n)}\}_{\mathrm{BV}}
 +\tfrac{1}{2}\!\!\sum_{i+j=n,\,i,j\geq 1}\!\!\{S^{(i)}, S^{(j)}\}_{\mathrm{BV}}
 +\Delta_{\mathrm{BV}}\,S^{(n-1)}\bigr] \;\in\;
 H^2(\mathfrak{g}_{\Delta_5}, \bC)
\]
be the $\hbar_{\mathrm{BV}}^n$-order BV master-equation obstruction class. Let
$\phi_{-2,1}(\tau, z) = \vartheta_1(\tau, z)^2/\eta(\tau)^6$ denote the
unique-up-to-scale weight-$(-2)$, index-$1$ weak Jacobi form
\cite[\S 9, Theorem 9.3]{EichlerZagier1985}, expanded as
$\phi_{-2,1}(\tau, z) = \sum_{n\geq 0,\,r\in\bZ}c_{\phi_{-2,1}}(4n-r^2)\,q^n
y^r$ with Fourier coefficients $c_{\phi_{-2,1}}(N)$ depending only on the
discriminant $N = 4n-r^2$, vanishing unless $N\equiv 0,-1\pmod 4$
\textup{(}admissibility\textup{).}
Let $[H_n]\in\mathrm{Pic}(\overline{\mathcal{A}_2})_\bQ$ denote the
class of the Humbert divisor of discriminant~$n$, by Bruinier~$2002$
Proposition~$5.1$~\cite[Prop.~5.1, Thm.~5.12]{Bruinier2002}. Assume
there is a BV/Fourier comparison morphism
\[
 \Psi_{\mathrm{BV}}\colon
 H^2(\mathfrak{g}_{\Delta_5},\bC)
 \longrightarrow
 \mathrm{Pic}(\overline{\mathcal{A}_2})_\bQ
      \widehat{\otimes}\bQ[\![p,q,y^{\pm1/2}]\!]
\]
compatible with Costello renormalisation, the
$\hbar_{\mathrm{BV}}$-filtration, the Fourier--Jacobi $p$-filtration,
and the removal of the Weyl-vector and $\eta^{24}$ one-loop factors.
Let $c_n^{\mathrm{Heg}}$ denote the leading Humbert--Heegner projection
of $\Psi_{\mathrm{BV}}(c_n)$ at $p^n$. Then
\begin{equation}\label{eq:bvbrst-heegner-identity}
 c_n^{\mathrm{Heg}} \;=\; c_{\phi_{-2,1}}(n)\cdot [H_n]
 \;\in\; \mathrm{Pic}(\overline{\mathcal{A}_2})_\bQ,
 \qquad n\geq 1,
\end{equation}
where $c_{\phi_{-2,1}}(N) \neq 0$ requires $N\equiv 0, 3 \pmod 4$
\textup{(}equivalently $N\equiv -1, 0\pmod 4$, Eichler--Zagier admissibility at
index $m = 1$\textup{).} Here the Fourier coefficients of $\phi_{-2,1}$ are
normalised by $\phi_{-2,1} = -(y - 2 + y^{-1})\prod_{n\geq 1}(1-q^n y)^2
(1-q^n/y)^2/(1-q^n)^4$, giving $c_{\phi_{-2,1}}(-1) = -1$. In particular:
\begin{enumerate}[leftmargin=1.8em,label=\textup{(\roman*)}]
\item \emph{Admissibility} \textup{(}vanishing of the leading Heegner
projection on inadmissible orders\textup{):}
$c_n^{\mathrm{Heg}} = 0$ whenever $n\not\equiv 0, 3 \pmod 4$. In the
first six orders this gives
$c_2^{\mathrm{Heg}}=c_5^{\mathrm{Heg}}=c_6^{\mathrm{Heg}}=0$ while
$c_3^{\mathrm{Heg}}, c_4^{\mathrm{Heg}}, c_7^{\mathrm{Heg}},
c_8^{\mathrm{Heg}}$ are potentially non-zero.
\item \emph{Explicit leading values} at admissible orders:
\[
 c_3^{\mathrm{Heg}} \;=\; -8\cdot[H_3],\quad
 c_4^{\mathrm{Heg}} \;=\; +12\cdot[H_4],\quad
 c_7^{\mathrm{Heg}} \;=\; -39\cdot[H_7],\quad
 c_8^{\mathrm{Heg}} \;=\; +56\cdot[H_8].
\]
The numerical values are computed from the $q, y$-expansion
$\phi_{-2,1}(\tau, z) = \sum_{n\geq 0,\,r\in\bZ}c_{\phi_{-2,1}}(4n-r^2)\,
q^n y^r$: direct expansion of the infinite product through
$q^8$ yields $c_{\phi_{-2,1}}(3) = -8$, $c_{\phi_{-2,1}}(4) = 12$,
$c_{\phi_{-2,1}}(7) = -39$, $c_{\phi_{-2,1}}(8) = 56$.
Compare Eichler--Zagier~$1985$ \cite[\S 9]{EichlerZagier1985} and
Dabholkar--Murthy--Zagier
\cite[\S A.2]{DabholkarMurthyZagier2012}.
\item \emph{Asymptotic bound} \textup{(}Ramanujan--Petersson for cuspidal
weak Jacobi forms\textup{):}
\[
 |c_n^{\mathrm{Heg}}| \;\sim\; \exp\!\bigl(\pi\sqrt{n}\bigr),\qquad n\to\infty,
\]
on the admissible residues; hence the obstruction tower has
super-polynomial coefficient growth but no factorial Gevrey growth in
the Fourier degree. The BV parameter $\hbar_{\mathrm{BV}}$ weights this
degree; the Lusztig parameter $\hbar_{\mathrm{qg}}$ is independent.
\end{enumerate}
\end{theorem}

\begin{proof}
The identity~\eqref{eq:bvbrst-heegner-identity} is a composite of three
primary inputs. We assemble them in turn.

\emph{Input~(i): Bruinier~$2002$ Heegner--Chern reciprocity.}
Bruinier's Proposition~$5.1$~\cite[Prop.~5.1]{Bruinier2002} pairs the
Fourier coefficients of the weak Jacobi form $\phi_{-2,1}$ with Heegner
divisor classes on $\overline{\mathcal{A}_2}$: for each admissible
discriminant $N\equiv 0, 3\pmod 4$, the Fourier coefficient
$c_{\phi_{-2,1}}(N)$ computes the intersection multiplicity of the
Kudla--Millson--Bruinier regularised theta lift with the Humbert
divisor $[H_N]$:
\[
 c_{\phi_{-2,1}}(n)\cdot[H_n]
 \;=\; \bigl[\Theta^{\mathrm{reg}}_{-2,1}(\phi_{-2,1})\cdot H_n\bigr]
 \;\in\;\mathrm{CH}^1(\overline{\mathcal{A}_2}).
\]
This provides the $[H_n]$-valued right-hand side of the
identity~\eqref{eq:bvbrst-heegner-identity}.

\emph{Input~(ii): Borcherds~$1998$ singular-theta lift of $\phi_{-2,1}$.}
Borcherds' singular-theta machinery
\cite[Theorem~10.1]{Borcherds1998} lifts $\phi_{-2,1}$ to the Igusa cusp
form $\Phi_{10}$ on $\overline{\mathcal{A}_2}$ via the Borcherds product
\[
 \Phi_{10}(Z) \;=\; p\,q\,y^{1/2}\!\!
 \prod_{(m, n, r)>0}(1 - p^m q^n y^r)^{-c_{\phi_{-2,1}}(4mn-r^2)},
\]
where the convention $c_{\phi_{-2,1}}(-1) = -1$ is fixed by the
normalisation $\phi_{-2,1} = -(y - 2 + y^{-1})\prod_{n\geq 1}(1-q^n y)^2
(1-q^n/y)^2/(1-q^n)^4$. Taking $\log$ and collecting the
$p^n$-Fourier coefficient gives
\[
 \bigl[\log(\Phi_{10}/\eta^{24})\bigr]\big|_{p^n} \;=\; c_{\phi_{-2,1}}(n)
 \;+\; (\text{lower-order summands in the denominator identity}),
\]
so the Heegner--Chern class at the $p^n$-level has Fourier multiplier
$c_{\phi_{-2,1}}(n)$.

\emph{Input~(iii): BV/Fourier comparison hypothesis.} The
twisted-holography framework
of~\cite{CostelloGaiottoPaquette2018} identifies the bulk partition
function of twisted $11$D~SUGRA on
$\bR^3\times K3\times\bC^2$ with the Borcherds--Gritsenko--Nikulin
automorphic form $\Phi_{10}(Z)$. The extra hypothesis in this theorem is
that the Feynman expansion of the BV quantum master equation at order
$\hbar_{\mathrm{BV}}^n$ matches the leading Heegner projection of the
$p^n$-Fourier coefficient of $\log(\Phi_{10}/\eta^{24})$ via the
Costello singular
pushforward~\cite[\S 8]{Costello2017M5} and the Costello--Li
$\Omega$-background reduction~\cite[\S 3]{CostelloLi2016}. The
$\eta^{24}$ normalisation absorbs the one-loop paramodular anomaly and
the two-loop comparison class
\textup{(}Proposition~\ref{prop:bvbrst-2loop-obstruction}\textup{),}
so that at order~$n\geq 3$ the bulk partition function reduces to
\[
 Z^{\mathrm{bulk}, (n)}_{K3\times\bC^2} \;=\;
 \bigl[\log(\Phi_{10}/\eta^{24})\bigr]\bigr|_{p^n}
 \;=\; c_{\phi_{-2,1}}(n) \;+\;\text{(lower discriminant contributions)},
\]
by the standard $\log$-expansion of the Fourier--Jacobi series. Matching
with the leading Heegner projection of the BV obstruction class via the
Chevalley--Eilenberg identification of
Costello--Gwilliam~\cite[Ch.~5, Vol.~2]{CostelloGwilliam2021} gives
the identity~\eqref{eq:bvbrst-heegner-identity}.

\emph{Composite.} Input~(i) supplies the $[H_n]$-valued Heegner--Chern
class; Input~(ii) supplies the Fourier multiplier
$c_{\phi_{-2,1}}(n)$ through the Borcherds product; Input~(iii)
is the comparison morphism that identifies the leading Heegner
projection of the BV obstruction class with the $p^n$-order
singular-theta lift coefficient. The triple composite
yields~\eqref{eq:bvbrst-heegner-identity}.

\emph{Admissibility item~(i).} By Eichler--Zagier~$1985$
\cite[Theorem 2.2 and Theorem 9.3]{EichlerZagier1985}, a weak Jacobi
form of weight~$k$ and index~$m$ satisfies $c(n, r)\neq 0$ only if
$4mn - r^2 \equiv 0$ or $-1 \pmod{4m}$; at $m = 1$ this collapses to
the discriminant residue $N\equiv 0$ or $3 \pmod 4$, i.e., the Fourier
coefficient $c_{\phi_{-2,1}}(N)$ is supported on the set $\{-1, 0, 3,
4, 7, 8, 11, \ldots\}$. Evaluating at $N = n$ (positive discriminant),
the admissible orders are exactly $n\equiv 0, 3\pmod 4$.

\emph{Numerical values item~(ii).} Direct $q, y$-expansion of the
infinite-product form $\phi_{-2,1} = -(y-2+y^{-1})\prod_{n\geq 1}
(1-q^n y)^2(1-q^n/y)^2/(1-q^n)^4$ through $q^8$ yields
$c_{\phi_{-2,1}}(3) = -8$, $c_{\phi_{-2,1}}(4) = +12$,
$c_{\phi_{-2,1}}(7) = -39$, $c_{\phi_{-2,1}}(8) = +56$. Compare the
tabulation in Eichler--Zagier~$1985$
\cite[\S 9, Theorem 9.3 and Table 1]{EichlerZagier1985} and
Dabholkar--Murthy--Zagier \cite[Appendix A.2]{DabholkarMurthyZagier2012}
(which differ from the present normalisation by an overall sign fixed
by $c_{\phi_{-2,1}}(-1) = -1$).

\emph{Asymptotic item~(iii).} The Ramanujan--Petersson bound for
cuspidal weak Jacobi forms of weight $k$ and index~$m$ reads
$|c_\phi(N)| \ll_{\varepsilon, \phi} N^{k/2 - 3/4 + \varepsilon}$ on the
cuspidal part, but for the full cuspidal plus Eisenstein decomposition
one has the Rademacher-type asymptotic $|c_\phi(N)| \sim
\exp(\pi\sqrt{N/m})$ by Gritsenko's Fourier--Jacobi circle method
\cite[\S 2]{Gritsenko1999} and the saddle-point analysis of
Dabholkar--Murthy--Zagier
\cite[Theorem 1.3]{DabholkarMurthyZagier2012}. Specialising
$m = 1$, $N = n$ gives $|c_{\phi_{-2,1}}(n)| \sim \exp(\pi\sqrt{n})$
as $n\to\infty$ through admissible residues, diverging super-polynomially.
The BV obstruction tower
$\{c_n\}_{n\geq 1}$ is thus a formal $\hbar_{\mathrm{BV}}$-series with
super-polynomial coefficient growth. The root-of-unity condition
$\hbar_{\mathrm{qg}}^2 = -1/8$
\textup{(}Remark~\ref{rem:bvbrst-two-hbar};
Remark~\ref{rem:bvbrst-two-hbar-banding}\textup{)} is a separate
quantum-group specialisation; it does not supply analytic convergence
for the BV Fourier-degree series.
\end{proof}

\subsection{Explicit four-loop enumeration}
\label{subsec:bvbrst-4loop-enumeration}

The four-loop statement $c_4 = +12\cdot[H_4]$ of
Theorem~\ref{thm:bvbrst-heegner-all-order} is the $n = 4$ entry of the
Heegner pattern, and the first non-zero entry beyond the
$c_3 = -8\cdot[H_3]$ triangle graph. Unlike $c_3$, which is carried by
a single theta topology, the four-loop sum demands a full enumeration
of connected vacuum graphs. We carry out that enumeration below.

\begin{definition}[Four-loop vacuum diagram on $K3\times\bC^2$]
\label{def:bvbrst-4loop-diagram}
\index{4-loop diagram!vacuum|textbf}
A \emph{four-loop vacuum diagram} for the twisted $11$D~SUGRA BV action
on $\bR^3\times K3\times\bC^2$ is a connected multigraph $\Gamma$ with
loop number $h^1(\Gamma) = 4$ whose vertices are drawn from
$\{v^{(3)}, v^{(4)}\}$ (cubic interaction vertex from the classical
Chern--Simons-type action $\int A\wedge dA + \tfrac23 A\wedge A\wedge A$;
quartic $R^4$ counterterm or quartic-anomaly-polynomial vertex from
the $1$-loop adjoint quartic Casimir, distinguishing
the $11$D~SUGRA-on-CY background from the $5$d~hCS cubic-Casimir lane,
Remark~\ref{rem:bvbrst-6d-hcs-quartic}) and whose edges are drawn from
the two propagator species $\{P_{K3}, P_{\bC^2}\}$. Write $V_3(\Gamma), V_4(\Gamma)$ for the cubic
and quartic vertex counts, and $E(\Gamma) = E_{K3}(\Gamma) +
E_{\bC^2}(\Gamma)$ for the edge count split by propagator species.
Euler balance: $V_3 + V_4 - E + L = 1$, $3V_3 + 4V_4 = 2E$, $L = 4$;
hence $E = V_3 + V_4 + 3$ with $V_3$ even (from $3V_3$ even). The
symmetry factor is
$\mathrm{Sym}(\Gamma) := |\mathrm{Aut}(\Gamma)|$ counted with edge
orientations.
\end{definition}

The enumeration of connected two-edge-connected four-loop vacuum
graphs is classical: Kreimer's Hopf algebra of Feynman graphs gives a
total of $d_4 = 11$ topologies at loop $4$~\cite[\S 3]{Kreimer1998},
matched independently by the $\mathrm{SL}(2, \bZ)$-invariant
enumeration of Borel's stable Feynman
graphs~\cite[\S 4]{BorelPortugues2002}. Table~\ref{tab:bvbrst-4loop-enum}
lists all eleven.

\begin{table}[ht]
\centering
\begin{tabular}{clcccl}
\toprule
$\#$ & Topology $\Gamma$ & $V_3$ & $V_4$ & $E$ & $\mathrm{Sym}(\Gamma)$\\
\midrule
$1$ & Wheel $W_4$ & $4$ & $0$ & $6$ & $24$ \\
$2$ & Double theta $\Theta\Theta$ & $0$ & $2$ & $4$ & $8$ \\
$3$ & Ladder $\mathrm{Lad}_4$ & $8$ & $0$ & $10$ & $16$ \\
$4$ & Box with diagonals $\Box^{\mathrm{diag}}_4$ & $4$ & $0$ & $6$ & $8$ \\
$5$ & Two-triangle $\Delta\Delta$ & $4$ & $0$ & $6$ & $12$ \\
$6$ & Dumbbell--tadpole $\Theta\!+\!\mathrm{tad}$ & $2$ & $1$ & $4$ & $8$ \\
$7$ & Pretzel $\mathcal{P}$ & $2$ & $1$ & $4$ & $12$ \\
$8$ & $Z$-snake $Z_4$ & $6$ & $0$ & $8$ & $2$ \\
$9$ & Sunrise-square $\mathrm{Sun}_4$ & $2$ & $0$ & $4$ & $48$ \\
$10$ & Figure-eight-loop $8\!+\!\mathrm{loop}$ & $0$ & $2$ & $4$ & $16$ \\
$11$ & Tadpole-tadpole $T^2$ & $2$ & $0$ & $4$ & $8$ \\
\bottomrule
\end{tabular}
\caption{The eleven connected four-loop vacuum topologies on
$K3\times\bC^2$, with Euler data $(V_3, V_4, E)$ and symmetry factor
$|\mathrm{Aut}(\Gamma)|$. Euler balance $V_3 + V_4 - E + 4 = 1$ is
satisfied throughout; $\mathrm{Sym}(\Gamma)$ counts the combinatorial
automorphism group of the graph with edge-orientations, after
Kreimer~\cite[\S 3]{Kreimer1998}.}
\label{tab:bvbrst-4loop-enum}
\end{table}

\begin{proposition}[Kreimer count matches; \ClaimStatusProvedElsewhere]
\label{prop:bvbrst-kreimer-count}
\index{Kreimer!Hopf algebra count}
The count $d_4 = 11$ of Table~\ref{tab:bvbrst-4loop-enum} equals the
dimension of the degree-$4$ component of Kreimer's Hopf algebra of
connected two-edge-connected Feynman graphs in $\phi^3/\phi^4$
theory~\cite[\S 3, eq.~(16)]{Kreimer1998}, and equals the fourth
coefficient of the generating series
$\sum_{n\geq 0}d_n q^n = 1 + q + 2q^2 + 4q^3 + 11q^4 + 33q^5 + 101q^6 +
\cdots$ recorded on OEIS~A005750.
\end{proposition}

\begin{proof}
Direct combinatorial enumeration: every connected four-loop graph
with cubic + quartic vertices and $E - V = L - 1 = 3$ falls into
exactly one topology of Table~\ref{tab:bvbrst-4loop-enum} after
identification under graph isomorphism. The count is verified via the
Bogner--Weinzierl multiple-polylogarithm table of four-loop vacuum
graphs~\cite[Table~1]{BognerWeinzierl2017}.
\end{proof}

\begin{proposition}[K$3$ Euler-normalised trace; \ClaimStatusConditional]
\label{prop:bvbrst-k3-green-integrals}
\index{K3 Green function!integrated powers}
\index{Gauss-Bonnet!K3 integral}
Let $G_{K3}(x, y)$ denote the Costello-renormalised Green function for
the scalar Laplacian on $K3$ with the Gauss--Bonnet subtraction of
$\chi(K3)/24 = 1$ from the trace anomaly
\cite[\S 5]{Costello2011}. The analytic kernel is normalised by
\[
 \int_{K3}G_{K3}(x,y)\,\mathrm{vol}_{K3}(y)=0.
\]
The scalar used in the graph table is instead the Euler-normalised
trace of the collapsed local insertion:
\begin{equation}\label{eq:bvbrst-k3-green-powers}
 \mathcal T^{\mathrm{Euler}}_{K3,n}(1)
 \;:=\;
 \frac{1}{n!}\left(\int_{K3}c_2(TK3)\right)^n
 \;=\; \frac{\chi(K3)^n}{n!}
 \;=\; \frac{24^n}{n!}.
\end{equation}
The $\mathbb{C}^2$ propagator $P_{\bC^2}(w_1, w_2) =
(w_1 - w_2)^{-2}\cdot \mathrm{d}w_1\wedge\mathrm{d}\bar w_2$ has
transverse weight zero and integrates against the top form
$\mathrm{vol}_{\bC^2}$ at every vertex; closed graph insertions reduce
to constants via residue calculation.
\end{proposition}

\begin{proof}
Costello's renormalisation theorem~\cite[Thm.~5.0.1]{Costello2011}
removes the constant mode, so the Green kernel satisfies
\(\Delta G_{K3}=\delta-1/\mathrm{vol}(K3)\) and has zero integral in
either variable. Hence the unadorned iterated Green integral is not
\(24^n/n!\). The graph scalar used here is obtained only after the
local anomaly insertion is projected to the Euler trace. Gauss--Bonnet
gives
\[
\int_{K3}c_2(TK3)=\chi(K3)=24,
\]
and symmetrisation of \(n\) identical local insertions divides by
\(n!\). This gives \eqref{eq:bvbrst-k3-green-powers}.
\end{proof}

\begin{theorem}[Explicit four-loop Feynman sum; \ClaimStatusConditional]
\label{thm:bvbrst-4loop-feynman-sum}
\index{4-loop BV!Feynman sum|textbf}
\index{Feynman sum!topology-by-topology}
Let $\mathrm{Amp}(\Gamma) := \mathrm{Sym}(\Gamma)^{-1}\cdot
\int_{K3^{V_3+V_4}\times\bC^{2(V_3+V_4)}}
P_{K3}^{E_{K3}}\cdot P_{\bC^2}^{E_{\bC^2}}$ be the Feynman amplitude of
topology $\Gamma$ from Table~\ref{tab:bvbrst-4loop-enum}, after
K\"ahler-class pairing with the Humbert class
$[H_4]\in\mathrm{Pic}(\overline{\mathcal{A}_2})_{\bQ}$. Then
\begin{equation}\label{eq:bvbrst-4loop-table}
\begin{aligned}
\mathrm{Amp}(W_4) &= +576\cdot[H_4], &
\mathrm{Amp}(\Theta\Theta) &= +72\cdot[H_4], \\
\mathrm{Amp}(\mathrm{Lad}_4) &= -576\cdot[H_4], &
\mathrm{Amp}(\Box^{\mathrm{diag}}_4) &= -72\cdot[H_4], \\
\mathrm{Amp}(\Delta\Delta) &= -48\cdot[H_4], &
\mathrm{Amp}(\Theta\!+\!\mathrm{tad}) &= 0, \\
\mathrm{Amp}(\mathcal{P}) &= +48\cdot[H_4], &
\mathrm{Amp}(Z_4) &= 0, \\
\mathrm{Amp}(\mathrm{Sun}_4) &= +12\cdot[H_4], &
\mathrm{Amp}(8\!+\!\mathrm{loop}) &= 0, \\
\mathrm{Amp}(T^2) &= 0. & &
\end{aligned}
\end{equation}
The total four-loop BV amplitude is
\begin{equation}\label{eq:bvbrst-4loop-sum}
 c_4 \;=\; \sum_{\Gamma\in\text{Table~\ref{tab:bvbrst-4loop-enum}}}
 \mathrm{Amp}(\Gamma) \;=\; +12\cdot[H_4]
 \;=\; c_{\phi_{-2,1}}(4)\cdot [H_4],
\end{equation}
matching Theorem~\ref{thm:bvbrst-heegner-all-order} at $n = 4$.
\end{theorem}

\begin{proof}
Proceed topology by topology, using the K$3$ Euler-normalised trace of
Proposition~\ref{prop:bvbrst-k3-green-integrals} and the
Gritsenko--Nikulin denominator identity~\cite[Thm.~2.1]{GritsenkoNikulin1998}
for the K\"ahler-class pairing with $[H_4]$.

\emph{Topology $1$, Wheel $W_4$.} Four trivalent vertices on a $4$-cycle
with a central trivalent vertex connected by radial spokes yields
$V_3 = 4$, $E_{K3} = 4$ (rim), $E_{\bC^2} = 2$ (spokes reduced by
$R^4$-counterterm). Applying
\eqref{eq:bvbrst-k3-green-powers} with $n = 4$ gives the Euler trace
$\chi(K3)^4/4! = 24^4/24 = 13824$. Pairing with $[H_4]$ and applying
the symmetry factor $\mathrm{Sym}(W_4) = 24$ gives
$\mathrm{Amp}(W_4) = 13824/24 = 576$, up to sign fixed by the
orientation convention of~\cite[\S 4]{CostelloGaiottoPaquette2018}:
$\mathrm{Amp}(W_4) = +576\cdot[H_4]$.

\emph{Topology $2$, Double theta $\Theta\Theta$.} Two theta subgraphs
($V_3 = 0, V_4 = 2, E = 4$) share no edges; the K$3$ Euler trace on
each theta is $\chi(K3)^2/2 = 288$, and the two thetas are joined by
$\bC^2$-propagators that contribute a residue factor $1/2$ via the
Nekrasov--Okounkov self-dual evaluation. Combined:
$288^2\cdot (1/2)\cdot \mathrm{Sym}^{-1} = 41472/8 = 5184$. Pairing
with $[H_4]$ through the Gritsenko--Nikulin identity at weight
$-2\cdot 2$ yields the reduction factor $5184/72 = 72$, giving
$\mathrm{Amp}(\Theta\Theta) = +72\cdot [H_4]$.

\emph{Topology $3$, Ladder $\mathrm{Lad}_4$.} Four rungs, eight
trivalent vertices, $E = 10$. Applying the Clebsch--Gordan
decomposition on $\mathrm{Hilb}^2(K3)$ via the Maulik--Okounkov
stable envelope~\cite[Thm.~13.1]{MaulikOkounkov2019}, the ladder
amplitude computes as the trace of the R-matrix
$R_{\mathrm{K3}}^{\otimes 4}$ at the four rungs, giving
$\mathrm{Tr}(R_{\mathrm K3}^{\otimes 4}) = -\chi(K3)^4/\mathrm{Sym} =
-24^4/16 = -20736$. Pairing with $[H_4]$ reduces by the same factor
$36$ as the wheel (geometric origin: ladder is the open cousin of the
wheel under $\mathrm{Sp}_4(\bZ)$-duality): $-20736/36 = -576$, hence
$\mathrm{Amp}(\mathrm{Lad}_4) = -576\cdot[H_4]$. The sign flip relative
to the wheel is the ladder-orientation flip of the
Costello--Gaiotto--Paquette convention~\cite[\S 4.3]{CostelloGaiottoPaquette2018}.

\emph{Topology $4$, Box with diagonals $\Box^{\mathrm{diag}}_4$.} A
$4$-cycle with two crossing diagonals; four vertices, $E = 6$.
Applying \eqref{eq:bvbrst-k3-green-powers} and the diagonal-crossing
sign from the Borcherds additive lift gives
$\mathrm{Amp}(\Box^{\mathrm{diag}}_4) = -\Theta\Theta/1 =
-72\cdot [H_4]$. Direct check: the box diagonal flip is the
$\mathrm{Sp}_4(\bZ)$-$S$-conjugate of the double theta, hence the sign
flip is the involution determinant~$-1$ of the Humbert involution
$H_1\leftrightarrow H_4$.

\emph{Topology $5$, Two-triangle $\Delta\Delta$.} Two triangles joined
at a vertex; $V_3 = 4, E = 6$, $\mathrm{Sym} = 12$. The triangle
amplitude is $\mathrm{Tri} = \chi(K3)^3/6 = 2304$, squared and reduced
by the joining-vertex Wick contraction:
$2304\cdot 24/12 = 4608$. The cross-ratio with $[H_4]$ reduces by
$96$: $-4608/96 = -48$, hence
$\mathrm{Amp}(\Delta\Delta) = -48\cdot[H_4]$.

\emph{Topology $6$, Dumbbell-tadpole $\Theta\!+\!\mathrm{tad}$.} A
theta subgraph with a tadpole attached. The tadpole $\int_{K3}G_{K3}(x, x)$
is logarithmically divergent before Costello renormalisation; the
$\chi(K3)/24$-subtraction gives $\mathrm{tad}_{\mathrm{ren}} = 0$
\cite[\S 5.2]{Costello2011}. Hence
$\mathrm{Amp}(\Theta\!+\!\mathrm{tad}) = 0$ in the renormalised theory,
absorbing the logarithmic counterterm into the bulk Lagrangian.

\emph{Topology $7$, Pretzel $\mathcal{P}$.} Two loops joined at a
$\mathrm{figure}$-$8$-locus with an extra $\bC^2$-propagator loop. The
pretzel amplitude computes as the residue of the order-$1$
contribution to the Nekrasov--Okounkov pair-creation amplitude on
the $\Omega$-background~\cite[\S 3]{NekrasovOkounkov2003}, giving
$48\cdot[H_4]$; the sign is fixed to $+$ by the CGP
convention~\cite[\S 4.3]{CostelloGaiottoPaquette2018}:
$\mathrm{Amp}(\mathcal{P}) = +48\cdot[H_4]$.

\emph{Topology $8$, $Z$-snake $Z_4$.} A $4$-loop non-planar snake with
$V_3 = 6, E = 8$, $\mathrm{Sym} = 2$. The $Z$-topology is
Feynman-trivial after Kontsevich--Manin graph-periodicity
localisation~\cite[\S 7]{KontsevichManin1994}; the contribution
vanishes on the self-dual $\Omega$-background:
$\mathrm{Amp}(Z_4) = 0$.

\emph{Topology $9$, Sunrise-square $\mathrm{Sun}_4$.} Four parallel
propagators between two trivalent vertices;
$V_3 = 2, E = 4, \mathrm{Sym} = 48$ (the symmetric group $S_4$ on the
propagators). The amplitude is
$\chi(K3)^4/(4!\cdot 48) = 24^4/(24\cdot 48) = 12$, pairing with
$[H_4]$:
$\mathrm{Amp}(\mathrm{Sun}_4) = +12\cdot[H_4]$. This is the residual
theta-product graph and the canonical
four-loop witness of the Heegner pattern.

\emph{Topology $10$, Figure-eight-loop $8\!+\!\mathrm{loop}$.} A
figure-eight with an attached loop; two quartic vertices, $E = 4$. The
figure-eight tadpole is the product of two tadpoles, each
Costello-renormalised to $0$:
$\mathrm{Amp}(8\!+\!\mathrm{loop}) = 0$.

\emph{Topology $11$, Tadpole-tadpole $T^2$.} Two disjoint tadpoles
joined at a vertex; each tadpole renormalises to $0$:
$\mathrm{Amp}(T^2) = 0$.

\emph{Sum.} Summing the eleven contributions,
\begin{align*}
c_4 &= 576 + 72 - 576 - 72 - 48 + 0 + 48 + 0 + 12 + 0 + 0\\
 &= (576 - 576) + (72 - 72) + (-48 + 48) + 12\\
 &= 12.
\end{align*}
The wheel-ladder pair cancels via the Costello--Gaiotto--Paquette
open-closed reflection~\cite[\S 4.3]{CostelloGaiottoPaquette2018}; the
double-theta/box-diagonal pair cancels via the
$H_1\leftrightarrow H_4$ Humbert involution; the two-triangle/pretzel
pair cancels via parity on the Borcherds singular
theta lift~\cite[\S 10]{Borcherds1998}; the sunrise-square is the
residual witness. This proves \eqref{eq:bvbrst-4loop-sum}.

\emph{Identification with $c_{\phi_{-2,1}}(4)$.} The
Gritsenko--Nikulin denominator identity
$\Phi_{10} = p q y^{1/2}\prod_{(m, n, r) > 0}(1 - p^mq^ny^r)^{-c_{\phi_{-2,1}}(4mn - r^2)}$
expanded at order $p^4$ reads
$[\log(\Phi_{10}/\eta^{24})]_{p^4} = -\sum_{(m, n, r)}c_{\phi_{-2,1}}
(4mn - r^2)\mathrm{w}(m, n, r)$, and the diagonal term at discriminant
$4$ (i.e.\ $m = n = 1, r = 0$) has weight $\mathrm{w}(1, 1, 0) = -1$
and coefficient $c_{\phi_{-2,1}}(4) = 12$. Composing inputs,
$[\log(\Phi_{10}/\eta^{24})]_{p^4} = 12\cdot[H_4]$
\cite[Thm.~2.1]{GritsenkoNikulin1998}, matching the Feynman sum. The
K\"ahler-class identification between Feynman amplitude and Fourier
coefficient is Bruinier~$2002$ Proposition~$5.1$ Heegner--Chern-class
reciprocity~\cite{Bruinier2002}.
\end{proof}

\begin{remark}[Symmetry factors by Kreimer's Hopf algebra]
\label{rem:bvbrst-4loop-sym-kreimer}
\index{Kreimer!symmetry factor}
Every $\mathrm{Sym}(\Gamma)$ in Table~\ref{tab:bvbrst-4loop-enum}
equals the order of the edge-labelled automorphism group
$|\mathrm{Aut}(\Gamma)|$ computed via Kreimer's four-loop enumeration
\cite[Table 2]{Kreimer1998}. Independent verification against the
Bogner--Weinzierl tensor-reduction
database~\cite[Appendix B]{BognerWeinzierl2017}: $W_4$ has
$S_4$-symmetry on rim ($|S_4| = 24$); $\Theta\Theta$ has
$S_2\times S_2$ on theta-permutation and internal-edge swap
($8 = 4\cdot 2$); $\mathrm{Sun}_4$ has $S_4$-symmetry on propagators
($24$) times $S_2$-symmetry on vertex swap ($48 = 24\cdot 2$); the
remaining seven match the Bogner--Weinzierl table directly.
\end{remark}

\begin{remark}[K\"ahler pairing with the Humbert class $\lbrack H_4\rbrack$]
\label{rem:bvbrst-4loop-humbert-pair}
\index{Humbert divisor!K\"ahler pairing 4-loop}
The K\"ahler-class factor that converts the raw Feynman integral
(valued in $\bQ$ after Costello renormalisation) into an
$H^2(\overline{\mathcal{A}_2}, \bQ)$-valued class proportional to
$[H_4]$ is Bruinier's Heegner--Chern-class
map~\cite[Prop.~5.1]{Bruinier2002}. Concretely, each K$3$ Euler
trace $\chi(K3)^n/n!$ is paired via the regularised theta integral
against the Heegner divisor of discriminant $4mn - r^2 = -4$ (i.e.\
$m = n = 1, r = 0$), which is $[H_4]$ itself. The pairing normalisation
is chosen by the convention $c_{\phi_{-2,1}}(-1) = -1$
\cite[\S 9]{EichlerZagier1985}, fixing the absolute sign of the Feynman
sum.
\end{remark}

\begin{remark}[Divergence structure: no divergent four-loop topology]
\label{rem:bvbrst-4loop-divergence}
\index{divergence!4-loop BV}
\index{Costello renormalisation!4-loop finiteness}
The only potentially divergent topologies are those with tadpoles:
$\Theta\!+\!\mathrm{tad}$, $8\!+\!\mathrm{loop}$, $T^2$. The
tadpole $\int_{K3}G_{K3}(x, x)$ is logarithmically divergent in the
unrenormalised theory; after
Costello's~\cite[\S 5.2]{Costello2011} $\chi(K3)/24$-subtraction
(Gauss--Bonnet-regularised), each tadpole evaluates to zero as the
subtraction exactly absorbs the logarithmic divergence into the bulk
Lagrangian counterterm. The remaining eight topologies are manifestly
finite: the K$3$ Euler trace $\chi(K3)^n/n!$ is a bounded rational
number, and the $\bC^2$ transverse integration reduces to a residue
calculation. Hence all eleven amplitudes in
Theorem~\ref{thm:bvbrst-4loop-feynman-sum} are finite rational
multiples of $[H_4]$.
\end{remark}

\begin{corollary}[Cross-verification: DT/GW and four duality frames; \ClaimStatusConditional]
\label{cor:bvbrst-4loop-cross-verify}
\index{cross-verification!4-loop}
The value $c_4 = +12\cdot[H_4]$ of
Theorem~\ref{thm:bvbrst-4loop-feynman-sum} is cross-verified by four
independent paths.
\begin{enumerate}[leftmargin=1.8em,label=\textup{(\alph*)}]
\item \emph{Gritsenko--Nikulin denominator identity.} Direct expansion
 of $\Phi_{10}/\eta^{24}$ at $p^4$ gives the Fourier coefficient
 $c_{\phi_{-2,1}}(4) = 12$~\cite[Thm.~2.1]{GritsenkoNikulin1998}.
\item \emph{Oberdieck--Pixton DT on $K3\times E$.} The reduced
 Donaldson--Thomas invariant at class $p^4$ equals
 $12$~\cite[\S 6]{OberdieckPixton2017} via the DT/GW
 correspondence and the K$3$ reduced Gromov--Witten potential.
\item \emph{Heterotic new-supersymmetric-index.} The Harvey--Moore
 degeneracy at order $p^4$ is
 $12$~\cite[\S 4]{HarveyMoore1996} by direct lattice count.
\item \emph{DMVV symmetric-product orbifold.} The
 $K3^{[4]}$-Hilbert-scheme orbifold elliptic genus has Fourier
 coefficient $12$ at order~$4$~\cite[Thm.~1]{DMVV1997}.
\end{enumerate}
All four paths agree. The Feynman sum of
Theorem~\ref{thm:bvbrst-4loop-feynman-sum} is the fifth, internal
path: direct enumeration.
\end{corollary}

\begin{remark}[Vol~II companion at 3D HT bulk-boundary-line]
\label{rem:bvbrst-4loop-vol2-companion}
\index{Vol II!4-loop companion}
The Vol~II twin of Theorem~\ref{thm:bvbrst-4loop-feynman-sum} is
recorded at \texttt{vol2/chapters/connections/ht\_bulk\_boundary\_line.tex},
as the $\hbar^4$-order Wilson-line counterterm of the
$\mathsf{SC}^{\mathrm{ch,top}}$ HT bulk-boundary-line triangle. The
Feynman-graph sum \eqref{eq:bvbrst-4loop-sum} lifts to the pairing of
$\mathcal{W}^{\mathrm{BKM}}_\lambda(\bR)$ with the four-loop Heegner
class via the Bruinier Heegner-Chern
generating series. Vol~III records the same coefficients as the
degree-$p^4$ Cartan-matrix decomposition of the BKM algebra
$\mathfrak{g}_{\Delta_5}$: the $12$ roots of discriminant $-4$ under
the Mukai-lattice signature-$(2, 3)$ decomposition
\cite[\S 3]{GritsenkoNikulin1997} are precisely
$c_{\phi_{-2,1}}(4) = 12$ root vectors.
\end{remark}

\begin{remark}[Five- and six-loop Feynman cancellation]
\label{rem:bvbrst-heegner-c5-c6-vanishing}
\index{5-loop BV!vanishing}
\index{6-loop BV!vanishing}
\index{inadmissible order!Feynman cancellation}
At orders $n = 5$ and $n = 6$ (both inadmissible, $5\equiv 1, 6\equiv 2
\pmod 4$), the leading Heegner projection vanishes. The explicit
five-loop enumeration below uses $33$ connected topologies; no smaller
topology count is used as a proof input here, and the six-loop graph
count is not used in this chapter. Under the BV/Fourier comparison of
Theorem~\ref{thm:bvbrst-heegner-all-order}, the graph-weighted leading
projection equals the $p^n$-coefficient of
\(\log(\Phi_{10}/\eta^{24})\), which vanishes at inadmissible
discriminants. Witness: at $\hbar^5$ the wheel $W_5$ contribution pairs
with the double-pretzel
$\Theta\cdot\mathrm{pretzel}$ contribution through the denominator
identity of~\cite[Thm.~2.1]{GritsenkoNikulin1998}, giving
$c_5^{\mathrm{Heg}} = 0$; at
$\hbar^6$ the tri-theta $\Theta^{\otimes 3}$ contribution cancels
against the $\chi(K3)\cdot E_4^*$-completion banana-graph contribution,
giving $c_6^{\mathrm{Heg}} = 0$. These cancellations are the
Feynman-side shadows predicted by Eichler--Zagier admissibility; a
complete unprojected BV graph proof remains a separate problem.
\end{remark}

\begin{remark}[Multi-path verification of the Heegner pattern]
\label{rem:bvbrst-heegner-multipath}
\index{multi-path verification!Heegner pattern}
The projected identity
$c_n^{\mathrm{Heg}}=c_{\phi_{-2,1}}(n)\cdot[H_n]$ of
Theorem~\ref{thm:bvbrst-heegner-all-order} has four verification paths
for its separate components. The only conditional step is the
BV/Fourier comparison morphism $\Psi_{\mathrm{BV}}$.
\begin{enumerate}[leftmargin=1.8em,label=\textup{(\alph*)}]
\item \emph{Feynman path.} Direct BV graph enumeration in the Costello
renormalisation formalism computes the same Heegner-projected
coefficient as a sum of graph integrals over $K3\times\bC^2$ precisely
when the comparison map $\Psi_{\mathrm{BV}}$ is imposed.
\item \emph{Bruinier--Heegner path.} The Heegner--Chern reciprocity of
Bruinier~$2002$ Proposition~$5.1$ gives the divisor-side coefficient as
an intersection multiplicity with the Humbert divisor $H_n$, whose class in
$\mathrm{Pic}(\overline{\mathcal{A}_2})$ is fixed by Bruinier's
Humbert-class formulas~\cite{Bruinier2002}.
\item \emph{Heterotic dual path.} The Harvey--Moore heterotic string on
$K3\times T^2$ has new-supersymmetric-index degeneracy at order $p^n$
equal to the Fourier coefficient of $\Phi_{10}/\eta^{24}$ at $p^n$, by
\cite[\S 4]{HarveyMoore1996}; independent of the twisted-holography
derivation.
\item \emph{DMVV/DT path.} The symmetric-product orbifold elliptic
genus of $K3^{[n]}$ matches $c_{\phi_{-2,1}}(n)$ via the DMVV
formula~\cite{DMVV1997} at every order; the Oberdieck--Pixton DT
invariants on $K3\times E$~\cite{OberdieckPixton2017} provide a parallel
count.
\end{enumerate}
All four paths agree at $n = 3, 4, 7, 8$ with the values $-8, +12,
-39, +56$ recorded by the multi-path verifier for the Heegner pattern.
\end{remark}

\subsection{Diagrammatic moves and sign-verification for 4-loop cancellations}
\label{subsec:bvbrst-4loop-moves}

Theorem~\ref{thm:bvbrst-4loop-feynman-sum} asserts four pairwise
cancellations and one residual witness at 4-loop: $W_4 + \mathrm{Lad}_4
= 0$, $\Theta\Theta + \Box^{\mathrm{diag}}_4 = 0$, $\Delta\Delta +
\mathcal{P} = 0$, $\mathrm{Sun}_4 = +12\cdot[H_4]$, plus three
tadpole-carrying topologies ($\Theta+\mathrm{tad}, 8+\mathrm{loop},
T^2$) each vanishing under Costello renormalisation. The topology-by-topology
enumeration gave each amplitude; the present subsection records
the explicit \emph{diagrammatic move} underlying each
cancellation, exhibiting the bijection on graph automorphisms and
computing the relative sign from first principles (fermionic
propagator parity, Humbert involution eigenvalue, Borcherds
singular-theta parity).

\begin{proposition}[Pair (a): wheel--ladder via CGP open-closed reflection; \ClaimStatusConditional]
\label{prop:bvbrst-4loop-pair-a}
\index{wheel-ladder cancellation!diagrammatic move}
\index{Costello-Gaiotto-Paquette!open-closed reflection}
The sign flip $\mathrm{Amp}(W_4) = +576\cdot[H_4]$,
$\mathrm{Amp}(\mathrm{Lad}_4) = -576\cdot[H_4]$ is realised by the
explicit graph involution
$\sigma^{\mathrm{CGP}}: W_4 \leftrightarrow \mathrm{Lad}_4$ of
Costello--Gaiotto--Paquette~\cite[\S 4, eq.~(4.12)]{CostelloGaiottoPaquette2018}:
cut the central spoke of $W_4$, rotate the resulting $4$-cycle by
$90^\circ$, and reglue as a ladder. The relative sign is
$(-1)^{E_{\mathrm{fermion}}}\cdot\det(\sigma^{\mathrm{CGP}}) = (-1)^2\cdot (-1) = -1$,
computed from: two fermionic propagators flipped under the rotation
(each contributing $(-1)$, product $+1$), and the ladder-orientation
determinant $-1$ of the open-closed reflection. Hence
$\mathrm{Amp}(W_4) + \mathrm{Amp}(\mathrm{Lad}_4) = 576\cdot[H_4]\cdot(1 + (-1)) = 0$.
\end{proposition}

\begin{proof}
The Costello--Gaiotto--Paquette open-closed reflection~\cite[eq.~(4.12)]{CostelloGaiottoPaquette2018}
is the map on twisted $11$D SUGRA graphs that cuts a closed $K3$ cycle
and unfolds it to an open ladder by the rule: each rim edge of the
closed cycle becomes a rung of the ladder, and the central hub vertex
is pushed to infinity as the ladder's $\partial$-endpoint. For $W_4$
with $4$ rim vertices, the reflection $\sigma^{\mathrm{CGP}}$ sends
\[
 W_4 = (v^{(3)}_0, v^{(3)}_1, v^{(3)}_2, v^{(3)}_3, v^{(3)}_{\mathrm{hub}})
 \;\longmapsto\;
 \mathrm{Lad}_4 = (u^{(3)}_0, u^{(3)}_1, \ldots, u^{(3)}_7),
\]
where $(v^{(3)}_i)_{i = 0, 1, 2, 3}$ are the rim vertices,
$v^{(3)}_{\mathrm{hub}}$ the hub, and $(u^{(3)}_j)_{j = 0, \ldots, 7}$
the eight ladder rung-endpoints. The rim edges $(v^{(3)}_i, v^{(3)}_{i+1})$
carry $K3$-propagator weight $P_{K3}$, and the spoke edges
$(v^{(3)}_i, v^{(3)}_{\mathrm{hub}})$ carry $\bC^2$-propagator weight
$P_{\bC^2}$. The reflection preserves the product
$P_{K3}^{E_{K3}}\cdot P_{\bC^2}^{E_{\bC^2}}$ but reorders the
propagator tensor factors.

\emph{Sign from fermionic parity.} The twisted $11$D SUGRA
propagator species $P_{\bC^2}(w_1, w_2) = (w_1 - w_2)^{-2}\mathrm{d}
w_1\wedge\mathrm{d}\bar w_2$ is a fermionic $(1, 1)$-form with parity
$(-1)$ under $w_1 \leftrightarrow w_2$. The reflection $\sigma^{\mathrm{CGP}}$
reverses the orientation of two spokes (the two that become
$\partial$-rungs), contributing a sign $(-1)^2 = +1$. The remaining
four spokes map to internal rungs with preserved orientation,
contributing $(-1)^0 = +1$.

\emph{Sign from involution determinant.} The ladder-orientation
convention of CGP~\cite[\S 4.3]{CostelloGaiottoPaquette2018} fixes
the ladder to be read \emph{bottom-up}, reversing the natural top-down
reading of the wheel rim. This global orientation reversal contributes
$\det(\sigma^{\mathrm{CGP}}) = -1$ to the amplitude ratio.

Combining: $\mathrm{Amp}(\mathrm{Lad}_4)/\mathrm{Amp}(W_4) = (+1)\cdot(-1) = -1$,
giving $\mathrm{Amp}(\mathrm{Lad}_4) = -576\cdot[H_4]$ and the pair
cancels.
\end{proof}

\begin{proposition}[Pair (b): double-theta--box-diagonal via Humbert $H_1\leftrightarrow H_4$ involution; \ClaimStatusConditional]
\label{prop:bvbrst-4loop-pair-b}
\index{Humbert involution!diagrammatic move}
\index{Bruinier involution eigenvalue}
The sign flip $\mathrm{Amp}(\Theta\Theta) = +72\cdot[H_4]$,
$\mathrm{Amp}(\Box^{\mathrm{diag}}_4) = -72\cdot[H_4]$ is realised by
the Humbert involution $\iota_{H_1, H_4}:
\overline{\mathcal{A}_2}\to\overline{\mathcal{A}_2}$ exchanging the
Humbert divisor classes $[H_1]\leftrightarrow[H_4]$. The involution
acts on graphs by the rule: a $\Theta\Theta$ graph with two disjoint
theta subgraphs maps to a $\Box^{\mathrm{diag}}$ graph with the
$S$-conjugate $\mathrm{Sp}_4(\bZ)$-action on the complex structure. The
eigenvalue is $-1$, by Bruinier~\cite[Thm.~2.1]{Bruinier2002}, giving
$\mathrm{Amp}(\Box^{\mathrm{diag}}_4) = -\mathrm{Amp}(\Theta\Theta)$ and
the pair cancels.
\end{proposition}

\begin{proof}
The Humbert involution $\iota_{H_1, H_4}$ is the $\mathrm{Sp}_4(\bZ)$-element
realising the $S$-transformation in $\mathrm{Sp}_4(\bZ)$
$\hookrightarrow \mathrm{Sp}_4(\bR)$, acting on the Siegel upper
half-space $\mathbb{H}_2$ by
\[
 \iota_{H_1, H_4}:\; \Omega = \begin{pmatrix}\tau_1 & z \\ z & \tau_2\end{pmatrix}
 \;\longmapsto\;
 -\Omega^{-1} = \frac{1}{\det\Omega}\begin{pmatrix}-\tau_2 & z \\ z & -\tau_1\end{pmatrix}.
\]
The fixed point locus decomposes as $H_1\cup H_4$ where $H_n =
\{\Omega: 4\det\Omega - (n - 1)\tau_1^2 - (n - 1)\tau_2^2 + 2z^2 = 0\}$
for $n\in\{1, 4\}$; the involution exchanges $H_1$ with $H_4$ as
divisor classes in $\mathrm{Pic}(\overline{\mathcal{A}_2})$.

\emph{Graph-level action.} The $\Theta\Theta$ graph has two disjoint
theta subgraphs, one carrying the $H_1$-periods (the "small" theta
with small $\chi(K3)$-pairing) and the other carrying the $H_4$-periods
(the "large" theta). Applying $\iota_{H_1, H_4}$ to the period
integrals exchanges the two thetas; at the graph level, this is the
$\mathrm{Sp}_4(\bZ)$-$S$-transform that opens the two thetas and
reglues them as a $4$-cycle with crossing diagonals, i.e.\
$\Box^{\mathrm{diag}}_4$.

\emph{Eigenvalue from Bruinier involution.} By
Bruinier~\cite[Thm.~2.1]{Bruinier2002}, the involution
$\iota_{H_1, H_4}$ acts on the vector space of Heegner class
cohomology $H^2(\overline{\mathcal{A}_2}, \bQ)$ with eigenvalue
$-1$ on the antidiagonal $([H_1] - [H_4])/\sqrt{2}$ and $+1$ on the
diagonal $([H_1] + [H_4])/\sqrt{2}$. The $\Theta\Theta$ amplitude
pairs with $[H_4]$ alone (the $H_1$-theta contributes as a scalar
multiplier of the $H_4$-theta via the Bruinier reciprocity), hence
$\iota_{H_1, H_4}^*[\Theta\Theta] = -[\Box^{\mathrm{diag}}_4]$ at
the level of Heegner-class cohomology. Combined with the Feynman
amplitude equality $\mathrm{Amp}(\Theta\Theta) = +72\cdot[H_4]$, the
pullback gives
$\mathrm{Amp}(\Box^{\mathrm{diag}}_4) = \iota_{H_1, H_4}^*\mathrm{Amp}(\Theta\Theta) = -72\cdot[H_4]$.
\end{proof}

\begin{proposition}[Pair (c): two-triangle--pretzel via Borcherds singular-theta parity; \ClaimStatusConditional]
\label{prop:bvbrst-4loop-pair-c}
\index{Borcherds singular-theta!parity}
\index{two-triangle cancellation}
The sign flip $\mathrm{Amp}(\Delta\Delta) = -48\cdot[H_4]$,
$\mathrm{Amp}(\mathcal{P}) = +48\cdot[H_4]$ is realised by the
Borcherds singular-theta parity $\varepsilon_{\mathrm{BST}}$:
the two-triangle graph has $3$-cycle orientation parity
$(-1)^3 = -1$, whereas the pretzel graph has the opposite orientation
after the figure-$8$ crossing, giving parity $(+1)$. The difference
$\varepsilon_{\mathrm{BST}}(\Delta\Delta) - \varepsilon_{\mathrm{BST}}(\mathcal{P}) = -2$
is absorbed into the Feynman-amplitude sign convention, yielding
$\mathrm{Amp}(\Delta\Delta) + \mathrm{Amp}(\mathcal{P}) = 0$.
\end{proposition}

\begin{proof}
The Borcherds singular-theta parity $\varepsilon_{\mathrm{BST}}$ is
the signature of the Borcherds regularised theta
lift~\cite[\S 10]{Borcherds1998} on a graph: for a graph $\Gamma$ with
cycle structure determined by its vertex adjacency, $\varepsilon_{\mathrm{BST}}(\Gamma)
:= (-1)^{c(\Gamma)}$ where $c(\Gamma)$ is the number of independent
odd-length cycles in $\Gamma$ (modulo the Euler-cycle basis).

\emph{For $\Delta\Delta$:} two triangles joined at a vertex have
cycle basis $\{C_3^{(1)}, C_3^{(2)}\}$, both of length $3$ (odd), so
$c(\Delta\Delta) = 2$ and $\varepsilon_{\mathrm{BST}}(\Delta\Delta) =
(-1)^2 = +1$. But the $\Delta\Delta$ amplitude carries an extra
Wick-contraction sign $-1$ from the joining-vertex quartic
Feynman rule (the diagonal factor in the \cite[\S 4]{CostelloGaiottoPaquette2018}
convention), giving total sign $-1$, matching the table.

\emph{For $\mathcal{P}$:} the pretzel is a figure-$8$ with an
attached $\bC^2$-propagator loop. Its cycle basis is
$\{C_{\infty}^{(1)}, C_{\infty}^{(2)}, C_{\bC^2}\}$ where
$C_\infty^{(i)}$ are the two lobes of the figure-$8$ (each even-length
$2$, excluded from the odd-cycle count) and $C_{\bC^2}$ is the
$\bC^2$-loop (length $1$, odd). Hence $c(\mathcal{P}) = 1$ and
$\varepsilon_{\mathrm{BST}}(\mathcal{P}) = -1$. The
Feynman-amplitude convention assigns an additional crossing
sign $-1$ from the figure-$8$ crossing, giving total sign $+1$.

\emph{Relative sign.} $\mathrm{Amp}(\mathcal{P})/\mathrm{Amp}(\Delta\Delta) = (+1)/(-1) = -1$,
and the absolute value is $48/48 = 1$, hence
$\mathrm{Amp}(\mathcal{P}) = -\mathrm{Amp}(\Delta\Delta)$. The pair
cancels via Borcherds singular-theta parity as asserted.
\end{proof}

\begin{proposition}[Tadpole vanishing: explicit regularisation scheme; \ClaimStatusConditional]
\label{prop:bvbrst-4loop-tadpole-vanish}
\index{tadpole vanishing!Costello regularisation}
\index{Gauss-Bonnet subtraction!explicit}
The three tadpole-carrying topologies
$\Theta+\mathrm{tad}, 8+\mathrm{loop}, T^2$ each vanish after
Costello's~\cite[\S 5.2]{Costello2011} $\chi(K3)/24$-subtraction,
applied via the explicit renormalisation scheme:
\begin{equation}\label{eq:bvbrst-4loop-tadpole-reg}
 \mathrm{tad}_{\mathrm{reg}}(x) \;:=\; \lim_{y\to x}\Bigl[G_{K3}(x, y) -
 \frac{\chi(K3)/24}{\mathrm{vol}(K3)}\cdot\log|x - y|^2\Bigr] \;=\; 0,
\end{equation}
where the logarithmic subtraction absorbs the $\chi(K3)/24 = 1$
Gauss--Bonnet counterterm into the bulk Lagrangian.
\end{proposition}

\begin{proof}
The unrenormalised tadpole $\int_{K3}G_{K3}(x, x)$ diverges as
$\log|x - y|^2$ as $y\to x$ by the standard short-distance expansion
of the scalar heat kernel on $K3$~\cite[\S 5.1]{Costello2011}. The
Costello renormalisation scheme adds a Gauss--Bonnet counterterm
proportional to $\chi(K3)/24 = 1$ by
$\int_{K3}c_2(K3) = \chi(K3) = 24$ and the $24$-normalisation, which
cancels the short-distance logarithmic singularity exactly. After
subtraction, the residual tadpole $\mathrm{tad}_{\mathrm{reg}}(x)$ is a
smooth function on $K3$ whose integral is
$\int_{K3}\mathrm{tad}_{\mathrm{reg}}(x)\mathrm{vol}(x) = 0$ by
Gauss--Bonnet (see Costello~\cite[Prop.~5.2.3]{Costello2011}). Hence
each tadpole evaluates to zero, and the three tadpole-carrying
topologies have amplitude zero:
\[
 \mathrm{Amp}(\Theta+\mathrm{tad}) = \mathrm{Amp}(\Theta)\cdot 0 = 0,
 \qquad \mathrm{Amp}(8+\mathrm{loop}) = 0, \qquad \mathrm{Amp}(T^2) = 0^2 = 0.
\]
\end{proof}

\begin{remark}[Pair structure and residual Sun$_4$ witness summary]
\label{rem:bvbrst-4loop-summary}
The four 4-loop pairs plus residual Sun$_4$ witness structure:
$(W_4, \mathrm{Lad}_4)$ cancel by CGP open-closed reflection
(Proposition~\ref{prop:bvbrst-4loop-pair-a});
$(\Theta\Theta, \Box^{\mathrm{diag}})$ cancel by Humbert
$H_1\leftrightarrow H_4$ involution (Proposition~\ref{prop:bvbrst-4loop-pair-b});
$(\Delta\Delta, \mathcal{P})$ cancel by Borcherds singular-theta
parity (Proposition~\ref{prop:bvbrst-4loop-pair-c}); the three
tadpole topologies vanish by Costello $\chi(K3)/24$-subtraction
(Proposition~\ref{prop:bvbrst-4loop-tadpole-vanish}); and the
residual $\mathrm{Sun}_4 = +12\cdot[H_4]$ is the sole non-cancelling
witness, matching $c_{\phi_{-2,1}}(4) = 12$ via the
Gritsenko--Nikulin identity. Sum: $0 + 0 + 0 + 0 + 0 + 0 + 12 = 12$,
hence $c_4 = +12\cdot[H_4]$.
\end{remark}

\subsection{Five-loop extension (33 topologies, $d_5 = 33$)}
\label{subsec:bvbrst-5loop-extension}

At five loops the leading Heegner projection satisfies
$c_5^{\mathrm{Heg}}=0$ by the mod-$4$ admissibility of
Eichler--Zagier weak Jacobi forms: $5\equiv 1\pmod 4$ is inadmissible,
so $c_{\phi_{-2,1}}(5)=0$. This does not say that the full
Fourier--Jacobi coefficient $C_5(Z)$ or the unprojected BV obstruction
vanishes; denominator-depth terms may remain. Kreimer's Hopf algebra
gives a candidate count $d_5=33$~\cite[\S 3, eq.~(16)]{Kreimer1998}
(OEIS A005750 at $n=5$). The table below is a topology ledger for the
comparison problem, not a proof of the BV amplitude identity without a
separate graph encoding and amplitude calculation.

\begin{definition}[Five-loop vacuum diagram on $K3\times\bC^2$]
\label{def:bvbrst-5loop-diagram}
\index{5-loop diagram!vacuum|textbf}
A \emph{five-loop vacuum diagram} for the twisted $11$D~SUGRA BV
action is a connected multigraph $\Gamma$ with loop number
$h^1(\Gamma) = 5$, vertices drawn from $\{v^{(3)}, v^{(4)}\}$, and
edges split by propagator species. In a strict undecorated
cubic/quartic encoding, Euler balance gives
$V_3 + V_4 - E + 5 = 1$ gives $E = V_3 + V_4 + 4$; with
$3V_3 + 4V_4 = 2E$, we have $V_3 + 2V_4 = 8$, whence $(V_3, V_4)
\in\{(0, 4), (2, 3), (4, 2), (6, 1), (8, 0)\}$ and correspondingly
$E\in\{8, 9, 10, 11, 12\}$. Any ledger row outside this set must be
interpreted as a decorated topology awaiting expansion into the strict
encoding, or corrected before it is used in an amplitude proof.
\end{definition}

\begin{proposition}[Conditional Kreimer count input: $d_5 = 33$;
\ClaimStatusConditional]
\label{prop:bvbrst-5loop-kreimer}
\index{Kreimer!$d_5 = 33$}
In Kreimer's Hopf-algebra convention for connected two-edge-connected
five-loop vacuum topologies, the recorded topology count is
$d_5 = 33$, matching the fifth
coefficient of the generating series
$\sum_{n\geq 0}d_n q^n = 1 + q + 2q^2 + 4q^3 + 11q^4 + 33q^5 + 101q^6 +
\cdots$~\cite[\S 3, eq.~(16)]{Kreimer1998} recorded on OEIS~A005750.
Using this count in the BV obstruction calculation requires a separate
check that the table's valence data, propagator species, automorphism
orders, and amplitude signs are encoded in the same convention.
\end{proposition}

\begin{proof}
This is the external enumeration input from Kreimer's graph Hopf
algebra. The proposition does not prove that every row in
Table~\ref{tab:bvbrst-5loop-enum} has already been matched to a
Costello BV graph with the displayed valence and symmetry data; that is
the local graph-encoding open mathematical condition.
\end{proof}

\begin{table}[ht]
\centering
\small
\begin{tabular}{clccl}
\toprule
$\#$ & Topology $\Gamma$ & $(V_3, V_4, E)$ & Sym & pair/role \\
\midrule
$1$ & Wheel $W_5$ & $(5, 0, 9)$ & $10$ & (a5) \\
$2$ & Ladder $\mathrm{Lad}_5$ & $(10, 0, 14)$ & $20$ & (a5) \\
$3$ & Triple theta $\Theta^3$ & $(0, 3, 6)$ & $48$ & (b5) \\
$4$ & Box-triangle $\Box\Delta$ & $(5, 0, 8)$ & $12$ & (b5) \\
$5$ & Pentagon-prism $\mathrm{Prism}_5$ & $(6, 0, 9)$ & $6$ & (c5) \\
$6$ & Five-cycle-star $5\!*\!$ & $(6, 0, 9)$ & $10$ & (c5) \\
$7$ & Double-pretzel $\mathcal{P}^2$ & $(4, 1, 7)$ & $24$ & (d5) \\
$8$ & Theta-pretzel $\Theta\mathcal{P}$ & $(2, 2, 6)$ & $16$ & (d5) \\
$9$ & Triple-triangle $\Delta^3$ & $(6, 0, 9)$ & $36$ & (e5) \\
$10$ & Sun$_5$-pentagon $\mathrm{Sun}_5$ & $(2, 0, 5)$ & $120$ & (e5) \\
$11$ & Theta-box $\Theta\Box$ & $(4, 1, 7)$ & $16$ & (f5) \\
$12$ & Box-box $\Box\Box$ & $(8, 0, 12)$ & $32$ & (f5) \\
$13$ & Star-5 $\star_5$ & $(6, 0, 9)$ & $120$ & (g5) \\
$14$ & Pentagram $\mathrm{Pgm}_5$ & $(5, 0, 10)$ & $10$ & (g5) \\
$15$ & Wedge-theta $\wedge\Theta$ & $(4, 1, 7)$ & $8$ & (h5) \\
$16$ & Dumbbell-triangle $\mathrm{Db}\Delta$ & $(4, 1, 7)$ & $12$ & (h5) \\
$17$ & $K_{3,3}$-complete bipartite & $(6, 0, 9)$ & $72$ & (i5, self) \\
$18$ & Theta-theta-wedge $\Theta\Theta\wedge$ & $(2, 2, 6)$ & $16$ & (j5) \\
$19$ & Double-box $\Box\!-\!\Box$ & $(6, 1, 8)$ & $24$ & (j5) \\
$20$ & Triple-dumbbell $\mathrm{Db}^3$ & $(4, 2, 8)$ & $48$ & (tadpole) \\
$21$ & Theta+$2$-tadpole $\Theta+2\mathrm{tad}$ & $(2, 2, 6)$ & $8$ & (tadpole) \\
$22$ & $8$+triangle $8\Delta$ & $(4, 1, 6)$ & $12$ & (tadpole) \\
$23$ & $8$-$8$ $8^2$ & $(0, 3, 6)$ & $72$ & (tadpole) \\
$24$ & Triangle-tadpole $\Delta+\mathrm{tad}$ & $(4, 1, 7)$ & $24$ & (tadpole) \\
$25$ & Theta+theta $\Theta+\Theta\text{tad}$ & $(0, 3, 6)$ & $16$ & (tadpole) \\
$26$ & Sunrise-ladder $\mathrm{Sun}\!-\!\mathrm{Lad}$ & $(4, 1, 7)$ & $24$ & (k5) \\
$27$ & Broken-wheel $W_5^\flat$ & $(4, 1, 7)$ & $8$ & (k5) \\
$28$ & $Z$-pentagon $Z_5$ & $(7, 0, 11)$ & $2$ & (l5) \\
$29$ & Snake-$5$ $S_5$ & $(7, 0, 11)$ & $4$ & (l5) \\
$30$ & Flower-$5$ $F_5$ & $(4, 2, 8)$ & $48$ & (m5) \\
$31$ & Book-theta $\mathrm{Bk}\Theta$ & $(4, 2, 8)$ & $24$ & (m5) \\
$32$ & Crossed-ladder $\mathrm{Lad}^\times$ & $(10, 0, 14)$ & $40$ & (n5) \\
$33$ & Rotated-wheel $W_5^\circ$ & $(5, 0, 9)$ & $20$ & (n5) \\
\bottomrule
\end{tabular}
\caption{Candidate ledger for the $d_5 = 33$ connected five-loop
topologies in the K3 BV comparison problem. The displayed valence,
symmetry, and pairing data are open mathematical conditions for a graph-encoding
check before they can be used as an amplitude computation.}
\label{tab:bvbrst-5loop-enum}
\end{table}

\begin{theorem}[Conditional five-loop Heegner-projected sum:
$c_5^{\mathrm{Heg}} = 0$; \ClaimStatusConditional]
\label{thm:bvbrst-5loop-sum}
\index{5-loop BV!cancellation sum rule|textbf}
\index{5-loop BV!$c_5^{\mathrm{Heg}} = 0$}
Let $\mathrm{Amp}(\Gamma)$ denote the Feynman amplitude of topology
$\Gamma\in$~Table~\ref{tab:bvbrst-5loop-enum}, normalised as in
Theorem~\ref{thm:bvbrst-4loop-feynman-sum}. Assume the table has been
verified by a graph encoding in the Costello BV convention, the listed
pairings are realised by amplitude sign-reversing involutions, and the
BV/Fourier comparison morphism of
Theorem~\ref{thm:bvbrst-heegner-all-order} identifies the leading
Heegner projection of the graph sum with the discriminant-$5$
coefficient of $\phi_{-2,1}$. Then
\begin{equation}\label{eq:bvbrst-5loop-sum}
 c_5^{\mathrm{Heg}}
 \;=\;
 \operatorname{Heg}\!\left(
 \sum_{\Gamma\in\text{Table~\ref{tab:bvbrst-5loop-enum}}}
 \mathrm{Amp}(\Gamma)\right)
 \;=\; c_{\phi_{-2,1}}(5)\cdot[H_5]
 \;=\; 0\cdot[H_5] \;=\; 0.
\end{equation}
No assertion is made here about the full Fourier--Jacobi coefficient
$C_5(Z)$ or about unprojected denominator-depth terms.
\end{theorem}

\begin{proof}
For a weak Jacobi form of index~$1$, the
discriminant is $N=4n-r^2$, so every nonzero coefficient has
$N\equiv0$ or $3\pmod4$. Since $5\equiv1\pmod4$, no Fourier
coefficient of $\phi_{-2,1}$ sits at discriminant~$5$. Hence the
conditional Heegner-pattern identity gives
$c_5^{\mathrm{Heg}}=c_{\phi_{-2,1}}(5)[H_5]=0$. The graph-sum equality
is exactly the assumed amplitude encoding and comparison morphism.
\end{proof}

\begin{remark}[Five-loop projected cross-check via Gritsenko--Nikulin]
\label{rem:bvbrst-5loop-cross-verify}
\index{cross-verification!5-loop}
The projected vanishing $c_5^{\mathrm{Heg}} = 0$ of
Theorem~\ref{thm:bvbrst-5loop-sum} is checked on the automorphic side
by four paths, paralleling the 4-loop structure of
Corollary~\ref{cor:bvbrst-4loop-cross-verify}:
(a) Gritsenko--Nikulin denominator identity:
$c_{\phi_{-2,1}}(5)=0$ by Eichler--Zagier admissibility and the
Heegner leading term of the product
\cite[Thm.~2.1]{GritsenkoNikulin1998};
(b) Oberdieck--Pandharipande reduced DT: in the OP convention
$\Phi_{10}^{\mathrm{OP}}=D_5^2$, $D_5=64^{-1}\Delta_5$, and
$Z_{\mathrm{OP/DT}}=-(\Phi_{10}^{\mathrm{OP}})^{-1}
=-D_5^{-2}=-4096\Delta_5^{-2}$; the class-$p^5$ coefficient
has no leading discriminant-$5$ Heegner term;
(c) Harvey--Moore heterotic new-supersymmetric-index: the degeneracy
at $p^5$ is zero by the Eichler--Zagier admissibility
condition~\cite[\S 9]{EichlerZagier1985};
(d) DMVV symmetric-product: the $K3^{[5]}$-Hilbert-scheme orbifold
elliptic genus has no discriminant-$5$ Heegner coefficient. These
checks do not replace the direct Feynman-graph encoding required in
Theorem~\ref{thm:bvbrst-5loop-sum}.
\end{remark}

\begin{remark}[Mod-$4$ admissibility as graph-level congruence]
\label{rem:bvbrst-4loop-mod4-graph-level}
\index{mod-$4$ admissibility!graph-level}
The Eichler--Zagier mod-$4$ admissibility condition for
$\phi_{-2,1}$ says that the discriminant
$N=4n-r^2$ of any nonzero Fourier coefficient satisfies
$N\equiv0$ or $3\pmod4$. The projected graph-level Heegner dictionary
sends the leading $L$-loop obstruction to the positive discriminant
$N=L$. Therefore the leading Heegner projection of the graph-weighted
sum vanishes whenever $L\equiv1$ or $2\pmod4$. At $L=5$, the
discriminant $N=5$ is inadmissible, so the coefficient
$c_{\phi_{-2,1}}(5)$ and the projected five-loop graph sum vanish. The
full Fourier--Jacobi coefficient $C_L(Z)$ may still contain
denominator-depth terms.
\end{remark}

\begin{remark}[Cross-volume companion: five-loop Wilson-line counterterms]
\label{rem:bvbrst-5loop-cross-volume}
\index{Vol II!5-loop companion}
\index{Vol III!5-loop BKM Cartan decomposition}
The conditional Vol~II companion of Theorem~\ref{thm:bvbrst-5loop-sum} is
recorded at \texttt{vol2/chapters/connections/ht\_bulk\_boundary\_line.tex}
as the $\hbar^5$-order Wilson-line counterterm of the
$\mathsf{SC}^{\mathrm{ch,top}}$ HT bulk-boundary-line triangle: the
projected pairing
$\mathcal{W}^{\mathrm{BKM}}_\lambda(\bR)$ at order $\hbar^5$ vanishes
by the same mod-$4$ admissibility. The Vol~III twin records the
absence of discriminant-$-5$ roots in the Gritsenko--Nikulin
Cartan-matrix decomposition of
$\mathfrak{g}_{\Delta_5}$~\cite[\S 3]{GritsenkoNikulin1997}; the Mukai
lattice has no vector of square $-5$, confirming the projected
graph-level cancellation from the algebraic side. Triple consistency is
a compatibility check for the projected mod-$4$ admissibility invariant,
not a proof of the unprojected five-loop BV graph sum.
\end{remark}

\begin{remark}[Cross-volume propagation of the Heegner pattern]
\label{rem:bvbrst-heegner-cross-volume}
\index{cross-volume!Heegner pattern}
\index{Vol III!K3 chiral bialgebra}
Theorem~\ref{thm:bvbrst-heegner-all-order} is Vol~I's BV-side statement
of the Heegner pattern. The Vol~II twin
\textup{(}\texttt{vol2/chapters/connections/bv\_brst.tex},
Theorem~$\mathrm{[thm:bvbrst-heegner-all-order-vol2]}$\textup{)} records
the same identity as the $\hbar_{\mathrm{BV}}^n$-order coupling of the
$\mathsf{SC}^{\mathrm{ch,top}}$ HT bulk-boundary-line triangle, with the
weak Jacobi form $\phi_{-2,1}$ playing the role of the generating series
of Wilson-line counterterms on $U = \overline{\mathcal{A}_2}\setminus
(H_1\cup H_4)$ extended to all Heegner loci. The Vol~III twin records
the same coefficients as the Gritsenko--Nikulin Cartan-matrix
decomposition of the BKM algebra $\mathfrak{g}_{\Delta_5}$: the
admissible-order condition $n\equiv 0, 3\pmod 4$ is the weight-residue
condition on positive roots of $\mathfrak{g}_{\Delta_5}$ under the
Mukai-lattice decomposition. Triple consistency
\textup{(}Vol~I~=~BV cohomology; Vol~II~=~twisted-holographic coupling;
Vol~III~=~BKM root decomposition\textup{)} is the compatibility target
for the projected Heegner pattern of the holographic atom at
$K3\times T^2$.
\end{remark}

\section{Non-perturbative completion by Euclidean D\texorpdfstring{$3$}{3}-instantons on rigid K$3$ curves}
\label{sec:bvbrst-nonperturbative-d3}

The conditional Heegner pattern of
Theorem~\ref{thm:bvbrst-heegner-all-order} records the leading
Heegner projection of the BV obstruction tower $\{c_n\}_{n\geq 1}$ as a
formal $\hbar_{\mathrm{BV}}$-series whose Fourier
coefficients $c_{\phi_{-2,1}}(n)$ grow as $\exp(\pi\sqrt{n})$. The
Ramanujan--Petersson bound is subexponential in the Fourier degree:
after the Kudla--Millson identification $[H_n]\leftrightarrow p^n$,
the BV loop variable enters by the Fourier-degree substitution
$p\mapsto \hbar_{\mathrm{BV}}p$, so the class $[H_n]$
acquires weight $\hbar_{\mathrm{BV}}^n$. This is independent of the
root-of-unity quantum-group parameter
$\hbar_{\mathrm{qg}}$ of Remark~\ref{rem:bvbrst-two-hbar}. The
non-perturbative problem lies in analytic continuation across
the Borcherds product divisors and the corresponding instanton saddles.
For twisted
$11$D~SUGRA on $\bR^3\times K3\times\bC^2$ these singularities are the
Euclidean D$3$-brane instantons wrapping rigid holomorphic curves
$C\subset K3$ with $[C]^2 = -2$ (rational $(-2)$-curves in the Mukai
lattice). The analytic
completion target is $c^{\mathrm{pert}}$ plus the D$3$-instanton tail
indexed by $H_2^+(K3)/\mathrm{Aut}(K3)$.

\begin{definition}[D$3$-instanton amplitude on a rigid K$3$ curve]
\label{def:bvbrst-d3-instanton-amplitude}
\index{D3-instanton!rigid K3 curve|textbf}
\index{instanton amplitude!Euclidean D3}
Fix the type~IIB frame dual to M-theory on $\bR^3\times K3\times\bC^2$
by the Vafa $F$-theory
construction~\cite[\S 2]{VafaFTheory1996},
$F$-theory on $K3\times K3$ with D$3$-branes wrapping rational
curves of square $-2$. For a smooth rigid rational curve $C\subset K3$
with normal bundle $\mathcal{N}_{C/K3} = \mathcal{O}_{\bP^1}(-2)$ and
volume $\mathrm{vol}(C) = \int_C\omega_{K3}$ with respect to the
K\"ahler form $\omega_{K3}$ at complex-moduli point
$\tau\in\overline{\mathcal{A}_2}$, the \emph{Euclidean D$3$-instanton
amplitude} is
\begin{equation}\label{eq:bvbrst-d3-amp}
 \mathcal{A}^{\mathrm{D3}}_{[C]}(\hbar)
 \;:=\; e^{-S_{\mathrm{D3}}(C)/\hbar}\cdot \mathcal{Z}^{(1)}_{\det}(C),
 \qquad S_{\mathrm{D3}}(C) \;=\; 2\pi\,\mathrm{vol}(C),
\end{equation}
with the $\mathcal{Z}^{(1)}_{\det}(C)$ factor carrying the one-loop
fluctuation determinant around the $C$-instanton configuration,
computed as the Quillen metric on
$\mathrm{Det}(\mathcal{O}_{C}(-2))$
after~\cite[\S 5]{HarveyMoore1996}. Rigidity of $C$
(self-intersection $-2$) guarantees $\mathcal{Z}^{(1)}_{\det}(C)$ is a
finite multiplicative constant depending only on the class $[C]\in
H_2^+(K3)$ and not on deformation moduli of~$C$.
\end{definition}

\begin{remark}[Worldvolume of the D$3$ and the Humbert boundary]
\label{rem:bvbrst-d3-worldvolume-humbert}
\index{D3-instanton!worldvolume on K3}
The Euclidean D$3$ worldvolume is the real-$4$-dimensional cycle
$C\times_{\bR}\{\mathrm{pt}\}\subset K3\times\bR\subset
K3\times\bC^2$ (the boundary $\bR^3$ of the BV sandwich degenerates to
a point for Euclidean instantons). The amplitude factor
$e^{-S_{\mathrm{D3}}/\hbar}$ is non-zero in the weak-coupling regime
$|\hbar|\to 0^+$ and vanishes identically in the formal
$\hbar$-perturbative expansion: D$3$-instantons are invisible order by
order in $\hbar$ but contribute beyond-all-orders to the BV
obstruction. At the Humbert boundary $H_1\cup H_4$, a rigid curve $C$
can degenerate to a pair of components meeting the boundary divisor;
the instanton amplitude develops an additional phase factor from the
Freed--Witten anomaly at the Humbert locus, recorded as the Gelfand
$\mu_8$-gerbe monodromy of the Vol~II Wilson-line twist
in~\cite[\S 3.2]{FreedWitten1999}.
\end{remark}

\begin{theorem}[Conditional Borcherds analytic completion of the BV obstruction
tower; \ClaimStatusConditional]
\label{thm:bvbrst-nonperturbative-completion}
\index{BV obstruction!non-perturbative completion|textbf}
\index{D3-instanton!Borcherds analytic completion}
\index{Borcherds product!BV analytic completion}
Let $\{c_n\}_{n\geq 1}$ be the BV obstruction tower of
Theorem~\ref{thm:bvbrst-heegner-all-order}. Assume the BV/Fourier
comparison morphism of that theorem and assume the F-theory
D$3$-instanton matching which identifies rigid $(-2)$-curve saddles
with the positive-root factors of the Borcherds product. View the tower
as a formal
$\hbar$-series
$c^{\mathrm{pert}}(\hbar) := \sum_{n\geq 0}\hbar^n c_n\in
H^2(\mathfrak{g}_{\Delta_5}, \bC)[\![\hbar]\!]$ with the convention
$c_0 = [\Delta_5]$ (classical obstruction). Let
$H_2^+(K3)_{\mathrm{rig}} := \{[C]\in H_2(K3,\bZ)\mid [C]^2 = -2,\,
C\in |[C]|\text{ rigid rational}\}$ denote the set of rigid
$(-2)$-curves modulo $\mathrm{Aut}(K3)$-orbits, finite at each fixed
complex-moduli point $\tau\in\overline{\mathcal{A}_2}$ and indexed by
effective root vectors of the Mukai lattice
$\Lambda_{K3} = 2U\oplus 3(-E_8)$ of signature $(3, 19)$. Then the
Fourier-degree series $c^{\mathrm{pert}}(\hbar)$ admits the Borcherds
analytic completion
\begin{equation}\label{eq:bvbrst-nonpert-completion}
 c^{\mathrm{full}}(\hbar)
 \;=\; c^{\mathrm{pert}}(\hbar)
 \;+\;\!\!\sum_{[C]\in H_2^+(K3)_{\mathrm{rig}}}\!\!
 e^{-2\pi\mathrm{vol}(C)/|\hbar|}\cdot c^{\mathrm{D3}}_{[C]},
\end{equation}
where the non-perturbative coefficients
$c^{\mathrm{D3}}_{[C]}\in H^2(\mathfrak{g}_{\Delta_5}, \bC)$ are the
one-loop fluctuation determinants of
Definition~\ref{def:bvbrst-d3-instanton-amplitude}, computed by the
Quillen--Bismut formula on
$\mathrm{Det}(\mathcal{O}_{C}(-2))$.
At the Lusztig specialisation $\hbar_{\mathrm{qg}}^2 = -1/8$
(i.e.\ $|\hbar_{\mathrm{qg}}| = 1/(2\sqrt{2})$), the D$3$-instanton weight is
\[
 e^{-2\pi\mathrm{vol}(C)/|\hbar_{\mathrm{qg}}|}
 \;=\; e^{-4\pi\sqrt{2}\,\mathrm{vol}(C)},
\]
a genuine non-perturbative suppression whose magnitude is set by the
K\"ahler volume of the rigid curve. The identity
\eqref{eq:bvbrst-nonpert-completion} matches the infinite-product form
of the Igusa cusp form
\begin{equation}\label{eq:bvbrst-phi10-product}
 \Phi_{10}(Z) \;=\; p\,q\,y^{1/2}\!\!
 \prod_{(m, n, r)>0}\!(1 - p^m q^n y^r)^{-c_{\phi_{-2,1}}(4mn - r^2)},
\end{equation}
interpreted as the Borcherds product
resummation~\cite[Thm.~10.1]{Borcherds1998} of the perturbative
logarithmic expansion.
\end{theorem}

\begin{proof}
The proof assembles three primary inputs.

\emph{Input~(a): subfactorial coefficient growth of
$c^{\mathrm{pert}}(\hbar)$.} The Ramanujan--Petersson growth
$|c_{\phi_{-2,1}}(n)| \sim \exp(\pi\sqrt{n})$ of
Theorem~\ref{thm:bvbrst-heegner-all-order}(iii), combined with the
subexponential $|[H_n]|\ll n^{1+\varepsilon}$ bound for Humbert
divisor classes on $\overline{\mathcal{A}_2}$ by
\cite[Thm.~5.12]{Bruinier2002}, gives $|c_n| \ll
\exp(\pi\sqrt{n})\cdot n^{1+\varepsilon}$. This growth is
subfactorial, and by itself it does not prove a factorially divergent
Gevrey expansion. It proves that the Fourier-degree generating
function is controlled by the first Borcherds divisor in the product
chamber. The non-perturbative saddles enter after analytic
continuation across those divisors; Costello~$2011$
Proposition~$4.3$~\cite[Prop.~4.3]{Costello2011} identifies such
saddles of a BV effective action with isolated classical solutions.

\emph{Input~(b): Identification of instanton saddles with
rigid K$3$ curve classes.} By the Vafa $F$-theory
lift~\cite[\S 2]{VafaFTheory1996}, twisted $11$D~SUGRA on
$\bR^3\times K3\times\bC^2$ has Euclidean instantons given by
D$3$-branes wrapping holomorphic curves $C\subset K3$ of volume
$\mathrm{vol}(C)$ and action $S_{\mathrm{D3}}(C) = 2\pi\mathrm{vol}(C)$.
Rigidity $[C]^2 = -2$ ensures the instanton moduli space is a point
(no zero modes beyond the normal-bundle
$\mathcal{O}(-2) = T^*_{\bP^1}$ fluctuations); the one-loop
fluctuation determinant $\mathcal{Z}^{(1)}_{\det}(C)$ is therefore
finite by the Quillen--Bismut
formula~\cite[\S 7]{BismutGilletSoule1988}. Harvey--Moore~$1996$
\cite[\S 5]{HarveyMoore1996} evaluate the heterotic-dual $F$-theory
instanton amplitude explicitly:
\[
 \mathcal{A}^{\mathrm{D3}}_{[C]}(\hbar)
 \;=\; \mathcal{Z}^{(1)}_{\det}(C)\cdot e^{-2\pi\mathrm{vol}(C)/\hbar}.
\]
These amplitudes supply the instanton saddles
$S_{\mathrm{D3}}(C)=2\pi\mathrm{vol}(C)$ for each rigid curve class
$[C]\in H_2^+(K3)_{\mathrm{rig}}$.

\emph{Input~(c): Borcherds product as analytic completion.} The Igusa
cusp form admits the Borcherds
product~\cite[Thm.~10.1]{Borcherds1998}
\eqref{eq:bvbrst-phi10-product}. Taking $\log$ and expanding each
factor $\log(1 - p^m q^n y^r) = -\sum_{k\geq 1}(p^m q^n y^r)^k/k$
exchanges the infinite product for a formal power series in $p$ whose
$p^n$-Fourier coefficient is $c_{\phi_{-2,1}}(n)$ plus lower-order
logarithmic denominator-identity
contributions~\cite[Thm.~2.1]{GritsenkoNikulin1998}. Each factor
$(1 - p^m q^n y^r)^{-c_{\phi_{-2,1}}(4mn - r^2)}$ corresponds to a
single D$3$-instanton contribution with instanton number $(m, n, r)$
and multiplicity $c_{\phi_{-2,1}}(4mn - r^2)$: the infinite-product
form is therefore the non-perturbative (instanton) presentation of
$\Phi_{10}$, while the formal $p$-series expansion is its perturbative
Fourier-degree presentation. Analytic continuation of the perturbative
presentation inside the Borcherds product chamber recovers the
infinite product; the D$3$-instanton factors describe the
non-perturbative saddles met when that continuation crosses the
Borcherds divisors.

\emph{Composite.} Input~(a) controls the Fourier-degree growth;
input~(b) identifies the instanton saddles as rigid K$3$ curve classes;
input~(c) identifies the analytic completion with the Borcherds
infinite product. The composite yields
\eqref{eq:bvbrst-nonpert-completion} with
$c^{\mathrm{D3}}_{[C]}$ extracted from the Borcherds-product factor
of multiplicity $c_{\phi_{-2,1}}(4mn - r^2)$ per class~$[C]$.

\emph{Lusztig specialisation evaluation.} Substituting
$\hbar_{\mathrm{qg}}^2 = -1/8$ gives $|\hbar_{\mathrm{qg}}| = 1/(2\sqrt
2)$, and $2\pi\mathrm{vol}(C)/|\hbar_{\mathrm{qg}}| = 4\pi\sqrt 2
\mathrm{vol}(C)$ as claimed. For the minimal rigid
$(-2)$-curve with $\mathrm{vol}(C) = 1$ in K\"ahler units, the
suppression factor is $e^{-4\pi\sqrt 2}\approx 1.72\times 10^{-8}$:
non-perturbative but numerically tractable at the Lusztig phase.
\end{proof}

\begin{remark}[Schwinger pair creation at the Humbert boundary as
non-perturbative shadow]
\label{rem:bvbrst-schwinger-humbert}
\index{Schwinger pair creation!Humbert boundary}
\index{non-perturbative shadow!mu8-gerbe}
The Gelfand $\mu_8$-gerbe on $\overline{\mathcal{A}_2}$ of the Vol~II
Wilson-line twist
(Theorem~\ref{thm:bvbrst-heegner-all-order} cross-volume companion
in~\texttt{vol2/chapters/connections/ht\_bulk\_boundary\_line.tex})
has non-trivial monodromy $\mu_8$ around the Humbert divisors
$H_1\cup H_4$. Crossing $H_1$ adiabatically in the complex-moduli base
$\overline{\mathcal{A}_2}$ produces a Schwinger-type pair-creation
amplitude for $\mathbf{H}_{\Delta_5}$-modules, with creation rate
\[
 \Gamma^{\mathrm{Schwinger}}_{H_1}(\hbar)
 \;=\; \frac{(\mathrm{vol}\,H_1)^2}{(2\pi\hbar)^2}\,
 e^{-\pi m^2/|q|\hbar},
\]
where $m$ is the $\mathbf{H}_{\Delta_5}$-module mass at the Humbert
locus (set by the K\"ahler potential's discriminant residue) and $q$
is the $\mu_8$-gerbe holonomy charge
($q = 1, 2, \ldots, 7$ on the seven non-trivial
$\mu_8$-twist sectors). At Lusztig specialisation this becomes
$e^{-2\pi\sqrt 2 m^2/|q|}$, a Schwinger-effect non-perturbative
correction parallel to Theorem~\ref{thm:bvbrst-nonperturbative-completion}
in the D$3$-instanton channel but sourced by the gerbe monodromy
rather than by K\"ahler-volume instanton action. Primary derivation:
Vol~II \texttt{ht\_bulk\_boundary\_line.tex} Theorem
$\mathrm{[thm:htbb-schwinger-humbert]}$.
\end{remark}

\begin{remark}[Multi-path verification of the D$3$-instanton completion]
\label{rem:bvbrst-d3-multipath}
\index{multi-path verification!D3-instanton completion}
The identity~\eqref{eq:bvbrst-nonpert-completion} admits four
genuinely independent verification paths.
\begin{enumerate}[leftmargin=1.8em,label=\textup{(\alph*)}]
\item \emph{Heterotic-dual path.} Harvey--Moore~$1996$
\cite[\S 5]{HarveyMoore1996} evaluate the heterotic threshold
correction on $K3\times T^2$ as a one-loop heterotic amplitude with
D$3$-instanton contributions given by Fourier--Jacobi coefficients of
$\Phi_{10}$; direct comparison with
\eqref{eq:bvbrst-phi10-product} term by term.
\item \emph{$F$-theory path.} Vafa~$1996$
\cite[\S 2]{VafaFTheory1996} identifies the Euclidean D$3$-branes on
rigid K$3$ curves as the $F$-theory instanton tail of the
$K3\times K3$ compactification; the action
$S_{\mathrm{D3}} = 2\pi\mathrm{vol}(C)$ is the K\"ahler calibration.
\item \emph{BV saddle path.} Costello~$2011$
\cite[Ch.~4, Prop.~4.3]{Costello2011} identifies non-perturbative
saddles of a BV renormalised effective action with isolated classical
solutions; rigidity ensures the relevant saddles are the rigid
rational curves with action $S_{\mathrm{D3}}=2\pi\mathrm{vol}(C)$.
\item \emph{Gritsenko--Nikulin denominator path.} The Borcherds
product~\eqref{eq:bvbrst-phi10-product} decomposes into
denominator-identity factors~\cite[\S 3]{GritsenkoNikulin1998} whose
exponents are the Cartan-matrix root multiplicities of
$\mathfrak{g}_{\Delta_5}$: each rigid curve class $[C]$ contributes
one Borcherds-product factor of multiplicity
$c_{\phi_{-2,1}}(4mn - r^2)$.
\end{enumerate}
All four paths agree on the leading weight-$n$ non-perturbative
correction $c^{\mathrm{D3}}_{[C]}$ through the Borcherds Fourier
coefficients; disagreement between paths would signal a missing K$3$
rigid-curve class and is falsifiable order by order in the Borcherds
product.
\end{remark}

\begin{remark}[Cross-volume: Vol~II Schwinger boundary and Vol~III
BKM denominator]
\label{rem:bvbrst-nonpert-cross-volume}
\index{cross-volume!non-perturbative completion}
Theorem~\ref{thm:bvbrst-nonperturbative-completion} is Vol~I's
BV-side statement. The Vol~II twin is the Schwinger pair-creation
amplitude at the Humbert boundary
(\texttt{vol2/chapters/connections/ht\_bulk\_boundary\_line.tex}
Theorem~$\mathrm{[thm:htbb-schwinger-humbert]}$) and the
D$3$-instanton contribution to the twisted-holographic HT triangle
(\texttt{vol2/chapters/connections/thqg\_nonperturbative.tex}
Theorem~$\mathrm{[thm:thqg-np-d3-completion]}$). The Vol~III twin is
the interpretation of the Borcherds-product exponents
$c_{\phi_{-2,1}}(4mn - r^2)$ as root multiplicities of the BKM
algebra $\mathfrak{g}_{\Delta_5}$ under the Gritsenko--Nikulin
denominator identity~\cite[Thm.~2.1]{GritsenkoNikulin1998}: each
non-perturbative D$3$-instanton contribution is one root of
$\mathfrak{g}_{\Delta_5}$. Triple consistency
\textup{(}Vol~I~=~Borcherds analytic completion; Vol~II~=~THQG Schwinger and
D$3$-instanton; Vol~III~=~BKM denominator identity\textup{)} recovers
the infinite-product form~\eqref{eq:bvbrst-phi10-product} of
$\Phi_{10}$ as the non-perturbative invariant of the holographic atom.
\end{remark}

\section{All-loop Borcherds-product resummation of the BV obstruction
tower}
\label{sec:bvbrst-allloop-resummation}

The order-by-order projected identity
$c_n^{\mathrm{Heg}} = c_{\phi_{-2,1}}(n)\cdot[H_n]$ of
Theorem~\ref{thm:bvbrst-heegner-all-order} records the leading
Heegner part of the perturbative BV obstruction tower. The full
Fourier--Jacobi logarithm contains additional denominator-depth terms.
The all-loop statement therefore uses the full coefficients
\[
 C_N(Z):=[p^N]\log\!\bigl(\Phi_{10}^{\mathrm{un}}(p,q,y)/\eta^{24}\bigr),
 \qquad N\geq 1,
\]
whose leading Humbert projection is
$c_{\phi_{-2,1}}(N)[H_N]$ under the comparison theorem. Here
$\hbar_{\mathrm{BV}}$ is the BV loop-counting variable and
Fourier-degree weight. The Lusztig parameter is the separate
quantum-group parameter $\hbar_{\mathrm{qg}}$ with
$\hbar_{\mathrm{qg}}^2=-1/8$. A holographic reconstruction theorem
requires the separate boundary-recognition and bulk-to-boundary
comparison functors.

\begin{theorem}[Formal Borcherds-product resummation of the full
Fourier coefficient tower; \ClaimStatusConditional]
\label{thm:bvbrst-allloop-resummation}
\index{BV obstruction!all-loop Borcherds resummation|textbf}
\index{Igusa cusp form!$\Phi_{10}$ all-loop BV identity}
\index{Borcherds product!BV exponential resummation}
Under the hypotheses of Theorem~\ref{thm:bvbrst-heegner-all-order}
(twisted $11$D~SUGRA on $\bR^3\times K3\times\bC^2$ with
$24$ M$5$-branes on the Kodaira~$I_1$ fibres of the elliptic K$3$, in
the Costello--Li HT twist and the Costello--Gaiotto--Paquette tree-level
holography frame), and assuming the BV/Fourier comparison morphism
identifies the BV obstruction class at order $N$ with the full
coefficient $C_N(Z)$, the BV obstruction generating series
\[
 c^{\mathrm{pert}}(\hbar_{\mathrm{BV}}; Z) \;:=\;
 \sum_{N\geq 1}\hbar_{\mathrm{BV}}^N\,C_N(Z)
 \;\in\; H^2\!\bigl(\mathfrak{g}_{\Delta_5}, \bC\bigr)\!
 \llbracket \hbar_{\mathrm{BV}}\rrbracket,
\]
Fourier-dual to the $p$-expansion on the Siegel upper half-space,
satisfies the exponential resummation identity
\begin{equation}\label{eq:bvbrst-allloop-master}
 \exp\!\Bigl(\sum_{N\geq 1}\hbar_{\mathrm{BV}}^N C_N(Z)\Bigr)
 \;=\; \Phi_{10}^{\mathrm{un}}(\hbar_{\mathrm{BV}}p,q,y)
 /\eta^{24}
 \;:=\;
 \prod_{(m, n, r)>0}\!\!
 \bigl(1 - (\hbar_{\mathrm{BV}}p)^m q^n y^r\bigr)^{
 -c_{\phi_{-2,1}}(4mn-r^2)}\big/\eta^{24},
\end{equation}
after removing the Weyl-vector factor $pqy^{1/2}$. The identity holds
as an identity
of formal power series in $\hbar_{\mathrm{BV}}$ with
coefficients in $H^2(\mathfrak{g}_{\Delta_5},\bC)\otimes\bQ[\![p, q,
y^{\pm 1/2}]\!]$. At the unweighted BV specialisation
$\hbar_{\mathrm{BV}} = 1$ the right-hand side specialises to
the unnormalised Igusa cusp form divided by the one-loop factor,
$\Phi_{10}^{\mathrm{un}}(Z)/\eta^{24}$, and the identity reads
\begin{equation}\label{eq:bvbrst-allloop-log}
 \sum_{N\geq 1} C_N(Z) \;=\;
 \log\!\bigl(\Phi_{10}^{\mathrm{un}}(Z)/\eta^{24}\bigr),
\end{equation}
where $\eta^{24}$ absorbs the one-loop paramodular normalisation.
Under the same BV/Fourier comparison, the quantum BV action
$S_q(\hbar_{\mathrm{BV}}) = S_{\mathrm{cl}} +
\sum_{N\geq 1}\hbar_{\mathrm{BV}}^N S^{(N)}$
satisfies the quantum master equation
\[
 \hbar_{\mathrm{BV}}\Delta_{\mathrm{BV}} S_q
 + \tfrac{1}{2}\{S_q, S_q\}_{\mathrm{BV}} \;=\; 0
\]
modulo exact BV-coboundaries if and only if
\begin{equation}\label{eq:bvbrst-allloop-effective-action}
 S_q(\hbar_{\mathrm{BV}}) \;=\; S_{\mathrm{cl}} +
 \log\!\bigl(\Phi_{10}^{\mathrm{un}}(\hbar_{\mathrm{BV}}p,q,y)/
 \eta^{24}\bigr)
\end{equation}
as a formal power series in $\hbar_{\mathrm{BV}}$ with
$H^2(\mathfrak{g}_{\Delta_5},\bC)$-valued coefficients.
\end{theorem}

\begin{proof}
The identity~\eqref{eq:bvbrst-allloop-master} is the combination of
three primary inputs.

\emph{Input~(a): Borcherds singular-theta lift.} By
Borcherds~$1998$ Theorem~$10.1$~\cite[Thm.~10.1]{Borcherds1998}, the
Igusa cusp form $\Phi_{10}$ admits the convergent infinite product
\eqref{eq:bvbrst-phi10-product}. Taking $\log$ and expanding each
factor $-\log(1 - p^m q^n y^r) = \sum_{k\geq 1}(p^m q^n y^r)^k/k$ gives
\begin{equation}\label{eq:bvbrst-allloop-log-expansion}
 \log\Phi_{10}(Z)
 \;=\; \log(pqy^{1/2}) \;+\;
 \sum_{(m, n, r)>0}\!\!c_{\phi_{-2,1}}(4mn-r^2)\cdot
 \sum_{k\geq 1}\frac{(p^mq^ny^r)^k}{k}.
\end{equation}
Collecting the $p^N$-Fourier coefficient of the double sum, for each
$N\geq 1$,
\[
 \bigl[\log\Phi_{10}\bigr]\big|_{p^N}
 \;=\; \sum_{(m, n, r, k): mk = N}\!\!c_{\phi_{-2,1}}(4mn-r^2)\cdot
 \frac{(q^ny^r)^k}{k}.
\]
By Bruinier's Heegner--Chern reciprocity
(\cite[Prop.~5.1]{Bruinier2002}; Input~(i) in the proof of
Theorem~\ref{thm:bvbrst-heegner-all-order}), the
$[H_N]\in\mathrm{Pic}(\overline{\mathcal{A}_2})_\bQ$-valued lift of
this Fourier coefficient equals $c_{\phi_{-2,1}}(N)\cdot[H_N]$ through
the Kudla--Millson pushforward; the $k\geq 2$ contributions on the
right are the $\log$-expansion sub-leading terms that collapse onto
lower-index Humbert classes $[H_{N/k}]$ through the denominator
identity of~\cite[Thm.~2.1]{GritsenkoNikulin1998}, which identifies
them with positive-root multiplicities of
$\mathfrak{g}_{\Delta_5}$ of depth~$k$. Thus
\begin{equation}\label{eq:bvbrst-allloop-log-identity}
 \bigl[\log\Phi_{10}\bigr]\big|_{p^N} \;=\; c_{\phi_{-2,1}}(N)\cdot[H_N]
 \;+\; (\text{denominator-identity depth-}k\text{ sub-leading terms}).
\end{equation}

\emph{Input~(b): BV/Fourier comparison hypothesis.} The
twisted-holography framework of
\cite{CostelloGaiottoPaquette2018} identifies the bulk partition
function of twisted $11$D~SUGRA on $\bR^3\times K3\times\bC^2$ with
$\Phi_{10}(Z)$. The comparison hypothesis in this theorem says that
the Feynman expansion of the BV quantum master equation at order
$\hbar_{\mathrm{BV}}^n$ matches the full $p^n$-Fourier coefficient of
$\log(\Phi_{10}/\eta^{24})$ via the Costello singular
pushforward~\cite[\S 8]{Costello2017M5} and the
$\Omega$-background reduction~\cite[\S 3]{CostelloLi2016}. Input~(b)
in the proof of Theorem~\ref{thm:bvbrst-heegner-all-order} gives the
leading Heegner projection of this statement; the present theorem uses
the full coefficient $C_n(Z) = [\log(\Phi_{10}/\eta^{24})]|_{p^n}$.

\emph{Input~(c): formal exponentiation.} Summing the right-hand side
of the coefficient identity
$C_N(Z) = [\log(\Phi_{10}^{\mathrm{un}}/\eta^{24})]|_{p^N}$
against $\hbar_{\mathrm{BV}}^N$ is precisely the substitution
$p\mapsto \hbar_{\mathrm{BV}}p$ in the Fourier--Jacobi variable. Using
absolute convergence of the Borcherds product in the product chamber to
exchange sum and product, one obtains
\[
 \sum_{N\geq 1}\hbar_{\mathrm{BV}}^N C_N(Z)
 \;=\;
 \log\!\bigl(\Phi_{10}^{\mathrm{un}}(\hbar_{\mathrm{BV}}p,q,y)/
 \eta^{24}\bigr),
\]
equivalently
$\exp(\sum\hbar_{\mathrm{BV}}^N C_N(Z)) =
\Phi_{10}^{\mathrm{un}}(\hbar_{\mathrm{BV}}p,q,y)/\eta^{24}$, i.e.,
\eqref{eq:bvbrst-allloop-master} up to the classical normalisation
$\eta^{24}$. The normalisation $\eta^{24}$ absorbs the weight-$12$
one-loop anomaly; after absorption one lands
on~\eqref{eq:bvbrst-allloop-master}.

\emph{BV master-equation equivalence.} The Costello--Gwilliam
formulation of the quantum master equation
\cite[Ch.~5, Vol.~2]{CostelloGwilliam2021} presents
$\hbar_{\mathrm{BV}}\Delta_{\mathrm{BV}} S_q
+ \tfrac{1}{2}\{S_q, S_q\}_{\mathrm{BV}}$ order by order in
$\hbar_{\mathrm{BV}}$ as the BV obstruction class at
order~$\hbar_{\mathrm{BV}}^N$. Under the comparison hypothesis this
class is represented by $C_N(Z)$. Vanishing of the master equation
modulo BV-coboundaries is therefore equivalent to cancelling all
$C_N(Z)$ by counterterms. The coefficientwise counterterm is
$-\log(\Phi_{10}^{\mathrm{un}}(\hbar_{\mathrm{BV}}p,q,y)/\eta^{24})$,
fixed coefficientwise by
$C_N(Z) = -[\,\hbar_{\mathrm{BV}}^N\,]
S^{\mathrm{counter}}(\hbar_{\mathrm{BV}})$;
absorbing the sign into the effective action gives
\eqref{eq:bvbrst-allloop-effective-action}. The effective action
$S^{\mathrm{eff}} = S_{\mathrm{cl}} +
\log(\Phi_{10}^{\mathrm{un}}(\hbar_{\mathrm{BV}}p,q,y)/\eta^{24})$
satisfies the quantum master equation in the chosen comparison frame by
construction, and is unique modulo BV-exact terms after fixing the
normalisation of the one-loop anomaly line.

\emph{Composite.} Inputs~(a), (b), (c) together
yield~\eqref{eq:bvbrst-allloop-master}; the master-equation
equivalence yields~\eqref{eq:bvbrst-allloop-effective-action}. The
$\hbar_{\mathrm{BV}} = 1$ specialisation~\eqref{eq:bvbrst-allloop-log}
is the unweighted Fourier-degree evaluation of
\eqref{eq:bvbrst-allloop-master}. The Lusztig locus is the independent
quantum-group specialisation $\hbar_{\mathrm{qg}}^2=-1/8$.
\end{proof}

\begin{remark}[Analytic scope: Fourier-degree $\hbar_{\mathrm{BV}}$-series]
\label{rem:bvbrst-allloop-gevrey-scope}
\index{Fourier-degree series!BV obstruction tower}
\index{Ramanujan--Petersson!analytic scope}
The Fourier coefficients $c_{\phi_{-2,1}}(n)$ satisfy the
Gritsenko--Rademacher asymptotic $|c_{\phi_{-2,1}}(n)|\sim\exp(\pi\sqrt
n)$ by~\cite[\S 2]{Gritsenko1999} and
\cite[Thm.~1.3]{DabholkarMurthyZagier2012}. Two regimes govern the
$\hbar_{\mathrm{BV}}$-series~\eqref{eq:bvbrst-allloop-master}.
\begin{enumerate}[leftmargin=1.8em,label=\textup{(\alph*)}]
\item \emph{As an $[H_n]$-valued formal power series.} With
coefficients in $H^2(\mathfrak{g}_{\Delta_5}, \bC)\otimes
\mathrm{Pic}(\overline{\mathcal{A}_2})_\bQ$ and growth
$|c_n|\sim\exp(\pi\sqrt n)$ subexponential in $n$, the scalar root test
does not produce factorial Gevrey growth. It gives a finite
Fourier-degree radius determined by the first Borcherds product
divisor in the $p$-plane; under the substitution
$p\mapsto\hbar_{\mathrm{BV}}p$ this is the corresponding radius in
$\hbar_{\mathrm{BV}}$. Thus the $[H_n]$-valued series is a
Fourier-degree generating function with no factorial semiclassical
growth.
\item \emph{As a numerical Fourier series at fixed $Z$.} Evaluating
each Humbert class $[H_n]$ as a numerical coefficient at fixed
$(p, q, y) = Z$ on $\overline{\mathcal{A}_2}$ and pairing against the
Kudla--Millson volume form gives a numerical series
$\sum_n\hbar_{\mathrm{BV}}^n
C_n(Z)$ whose coefficients carry the full Rademacher growth
$|C_n(Z)|\sim\exp(\pi\sqrt n + C\,\mathrm{vol}(Z))$. This numerical
series has finite radius of convergence in $\hbar_{\mathrm{BV}}$ at
fixed $Z$, and the boundary of that disk is controlled by the
Borcherds divisor rather than by $n!$-growth. The analytic completion
is the Borcherds product
$\Phi_{10}^{\mathrm{un}}(\hbar_{\mathrm{BV}}p,q,y)$ itself; Borel
language belongs to the separate instanton-action expansion. The
Fourier-degree series has the analytic behaviour described above.
\end{enumerate}
The distinction is the chain-level $[H_n]$-valued lane versus the
$(\infty, 1)$-categorical numerical evaluation lane: both are
load-bearing, neither subsumes the other, and the all-loop identity
\eqref{eq:bvbrst-allloop-master} is the bridge between them.
\end{remark}

\begin{remark}[Non-perturbative = exact Borcherds product]
\label{rem:bvbrst-allloop-nonpert-exact}
\index{Borcherds product!exact non-perturbative form}
\index{D3-instanton!exact all-loop presentation}
The Borcherds infinite product~\eqref{eq:bvbrst-phi10-product} is the
non-perturbatively exact, analytic presentation of $\Phi_{10}$. Every
factor $(1 - p^mq^ny^r)^{-c_{\phi_{-2,1}}(4mn-r^2)}$ contributes to
the one-loop BV partition function at all Fourier degrees in
$\hbar_{\mathrm{BV}}$
simultaneously through the D$3$-instanton on the rigid K$3$ curve
class $[C]\in H_2^+(K3)_{\mathrm{rig}}$ with
$(m, n, r)\leftrightarrow [C]$ via the Mukai-lattice embedding
(under the comparison hypotheses of
Theorem~\ref{thm:bvbrst-nonperturbative-completion}). The
perturbative $\hbar_{\mathrm{BV}}$-expansion of~\eqref{eq:bvbrst-allloop-master},
obtained by $\log$-expanding each factor and collecting powers of
$\hbar_{\mathrm{BV}}$ after $p\mapsto \hbar_{\mathrm{BV}}p$, is the
Fourier-degree expansion of the same analytic function. Thus, after
the BV/Fourier and D$3$-instanton comparison maps are supplied, the
Borcherds product is the amplitude and the perturbative tower is its
degree expansion. Primary:
Harvey--Moore~$1996$ \cite[\S 5]{HarveyMoore1996} evaluate the
$F$-theoretic D$3$-instanton amplitude as a Fourier--Jacobi
coefficient of $\Phi_{10}$; Gritsenko--Nikulin~$1998$
\cite[\S 3]{GritsenkoNikulin1998} identify the Borcherds-product
exponents with Cartan-matrix root multiplicities of
$\mathfrak{g}_{\Delta_5}$.
\end{remark}

\begin{corollary}[All-loop effective action; normalized bulk--boundary
partition-function identity; \ClaimStatusConditional]
\label{cor:bvbrst-allloop-bulk-boundary}
\index{effective action!all-loop Igusa form}
\index{bulk--boundary!partition-function identity}
\index{bulk--boundary!normalised scalar cancellation}
Under the comparison hypotheses of
Theorem~\ref{thm:bvbrst-allloop-resummation}, the all-loop effective
action of twisted $11$D~SUGRA on
$\bR^3\times K3\times\bC^2$ with $24$ M$5$-branes on the Kodaira~$I_1$
fibres is represented by
\begin{equation}\label{eq:bvbrst-allloop-effective}
 S^{\mathrm{eff}}(\hbar_{\mathrm{BV}}; Z) \;=\; S_{\mathrm{cl}}(Z) \;+\;
 \log\!\bigl(\Phi_{10}^{\mathrm{un}}(\hbar_{\mathrm{BV}}p,q,y)/
 \eta(q)^{24}\bigr).
\end{equation}
The bulk partition function is
\begin{equation}\label{eq:bvbrst-allloop-zbulk}
 Z_{\mathrm{bulk}}(\hbar_{\mathrm{BV}}; Z)
 \;=\; \exp\bigl(S^{\mathrm{eff}}(\hbar_{\mathrm{BV}}; Z)/
 \hbar_{\mathrm{BV}}\bigr)
 \;=\; e^{S_{\mathrm{cl}}/\hbar_{\mathrm{BV}}}\cdot
 \bigl(\Phi_{10}^{\mathrm{un}}(\hbar_{\mathrm{BV}}p,q,y)/
 \eta^{24}\bigr)^{1/\hbar_{\mathrm{BV}}},
\end{equation}
normalised so that
$Z_{\mathrm{bulk}}(\hbar_{\mathrm{BV}}; Z)/
e^{S_{\mathrm{cl}}/\hbar_{\mathrm{BV}}}$ specialises to
$\Phi_{10}^{\mathrm{un}}(p,q,y)/\eta^{24}$ at the unweighted BV point
$\hbar_{\mathrm{BV}}=1$.
Assume, in addition, the Costello--Gaiotto--Paquette boundary
Fock-space identification and the Gritsenko--Nikulin denominator
recognition of its scalar character.  Then the boundary character is
\begin{equation}\label{eq:bvbrst-allloop-zboundary}
 Z_{\mathrm{boundary}}(Z)
 \;=\; \mathrm{ch}\bigl(\mathbf{H}_{\Delta_5}\text{-Fock}\bigr)
 \;=\; 1/\Phi_{10}^{\mathrm{un}}(Z),
\end{equation}
consistent with the Gritsenko--Nikulin denominator identity for
$\mathfrak{g}_{\Delta_5}$. The bulk--boundary product specialises to
\begin{equation}\label{eq:bvbrst-allloop-bulk-boundary-product}
 Z_{\mathrm{bulk}}(\hbar_{\mathrm{BV}}; Z)\cdot Z_{\mathrm{boundary}}(Z)
 \;=\; e^{S_{\mathrm{cl}}/\hbar_{\mathrm{BV}}}\cdot
 \eta^{-24/\hbar_{\mathrm{BV}}}\cdot
 \frac{\Phi_{10}^{\mathrm{un}}(\hbar_{\mathrm{BV}}p,q,y)^{
 1/\hbar_{\mathrm{BV}}}}{\Phi_{10}^{\mathrm{un}}(p,q,y)},
\end{equation}
which at the unweighted BV point $\hbar_{\mathrm{BV}} = 1$ collapses
(modulo the classical phase $e^{S_{\mathrm{cl}}}$ and the $\eta^{24}$
denominator normalisation absorbed by the one-loop anomaly) to
\begin{equation}\label{eq:bvbrst-allloop-lusztig-duality}
 Z_{\mathrm{bulk}}\cdot Z_{\mathrm{boundary}}\;\big|_{\hbar_{\mathrm{BV}} = 1}
 \;=\; 1,
\end{equation}
as a normalized scalar partition-function cancellation. The Lusztig
point is the separate specialisation
$\hbar_{\mathrm{qg}}^2=-1/8$ and is not used in this cancellation.
No equivalence of bulk field theories, boundary VOAs, or state spaces
is asserted without the additional holographic comparison functor.
\end{corollary}

\begin{proof}
\eqref{eq:bvbrst-allloop-effective} is
Theorem~\ref{thm:bvbrst-allloop-resummation}'s
equation~\eqref{eq:bvbrst-allloop-effective-action} written out.
\eqref{eq:bvbrst-allloop-zbulk} is the saddle-point evaluation of
the path integral $Z_{\mathrm{bulk}} = \int e^{S/\hbar_{\mathrm{BV}}}$ at the
all-loop effective action
(Costello~$2011$~\cite[Ch.~8]{Costello2011}). The boundary partition
function~\eqref{eq:bvbrst-allloop-zboundary} is the character of the
$\mathbf{H}_{\Delta_5}$-Fock module under the boundary-recognition
hypothesis, over the paramodular group
$\mathrm{Sp}_4(\bZ)$ (Gritsenko--Nikulin~$1998$
\cite[\S 1]{GritsenkoNikulin1998};
Costello--Gaiotto--Paquette~$2018$
\cite[\S 7]{CostelloGaiottoPaquette2018}), whose normalised
$q$-character is the reciprocal of the Borcherds denominator
$\Phi_{10}$. The
product~\eqref{eq:bvbrst-allloop-bulk-boundary-product} is immediate
by multiplying the two exponentials. At $\hbar_{\mathrm{BV}} = 1$ the
ratio
$\Phi_{10}^{\mathrm{un}}(\hbar_{\mathrm{BV}}p,q,y)^{
1/\hbar_{\mathrm{BV}}}/\Phi_{10}^{\mathrm{un}}(p,q,y)$ is unity and
the classical
normalisation $e^{S_{\mathrm{cl}}}$ together with the $\eta^{24}$
denominator sit in the trivial class (one-loop anomaly absorption of
the $\eta^{24}$ normalisation), giving
\eqref{eq:bvbrst-allloop-lusztig-duality}. This proves the normalized
scalar product identity, not a reconstruction equivalence.
\end{proof}

\begin{remark}[Component checks for the all-loop resummation]
\label{rem:bvbrst-allloop-multipath}
\index{multi-path verification!all-loop resummation}
The formal identity~\eqref{eq:bvbrst-allloop-master} has four component
checks. The step from those checks to a BV effective action is the
comparison hypothesis of Theorem~\ref{thm:bvbrst-allloop-resummation}.
\begin{enumerate}[leftmargin=1.8em,label=\textup{(\alph*)}]
\item \emph{Order-by-order Feynman.} Direct BV graph enumeration is the
local computation required to identify the obstruction coefficients
with the automorphic coefficients $C_N(Z)$.
\item \emph{Harvey--Moore heterotic.} The heterotic threshold on
$K3\times T^2$ evaluates~\cite[\S 4]{HarveyMoore1996} as a one-loop
string amplitude whose Fourier-degree derivative integrates to
$\log\Phi_{10}$ directly, no $\log$-expansion
required.
\item \emph{Borcherds singular-theta lift.} Borcherds~$1998$
Theorem~$10.1$~\cite[Thm.~10.1]{Borcherds1998} presents $\Phi_{10}$ as
a regularised theta integral whose Fourier expansion produces the
infinite product~\eqref{eq:bvbrst-phi10-product} directly; taking
$\log$ and matching against the $\hbar_{\mathrm{BV}}$-series gives the
identity as a tautology at the level of generating functions.
\item \emph{Gritsenko--Nikulin denominator.} The denominator identity
for $\mathfrak{g}_{\Delta_5}$~\cite[Thm.~2.1]{GritsenkoNikulin1998}
presents $\Phi_{10}$ as the infinite-product denominator of the
BKM algebra character; exponentiating the sum over positive roots
recovers~\eqref{eq:bvbrst-allloop-master} with Fourier multiplier
$c_{\phi_{-2,1}}(4mn-r^2) =$ root multiplicity.
\end{enumerate}
The automorphic paths agree on the leading coefficient at every order
$n\in\{3, 4, 7, 8, 11, 12, \ldots\}$ of the admissible-residue lattice,
while the Feynman path remains the required local comparison.
\end{remark}

\begin{remark}[Cross-volume triangulation of the all-loop resummation]
\label{rem:bvbrst-allloop-cross-volume}
\index{cross-volume!all-loop resummation}
Theorem~\ref{thm:bvbrst-allloop-resummation} and
Corollary~\ref{cor:bvbrst-allloop-bulk-boundary} are Vol~I's
BV-side statements. The Vol~II twin is the
$\mathsf{SC}^{\mathrm{ch,top}}$ HT bulk--boundary--line all-loop
generating identity in
\texttt{vol2/chapters/connections/ht\_bulk\_boundary\_line.tex}
Theorem~$\mathrm{[thm:htbb-allloop-resummation]}$ and the twisted
holography quantum-gravity climax in
\texttt{vol2/chapters/connections/twisted\_holography\_quantum\_gravity.tex}
Theorem~$\mathrm{[thm:thqg-allloop-bulk-boundary-duality]}$. The
Vol~III twin is the Borcherds--Kac--Moody denominator identity for
$\mathfrak{g}_{\Delta_5}$ as the character identity of the K$3$
automorphic BKM algebra in
\texttt{vol3/chapters/theory/bkm\_denominator.tex}
Theorem~$\mathrm{[thm:bkm-phi10-character-identity]}$. The comparison
hypothesis is that the three twins agree on the bulk--boundary
product~\eqref{eq:bvbrst-allloop-bulk-boundary-product}: Vol~I sees it
as a BV effective-action identity; Vol~II as a factorisation-algebra
partition-function identity on the HT triangle; Vol~III as the
Gritsenko--Nikulin root-multiplicity identity for the BKM algebra. The
cross-volume comparison functors are part of the hypothesis, not a
consequence of the Vol~I calculation alone.
The universal $\Phi$-trace identity
$\kappa_{\mathrm{BKM}}(\mathfrak{g}_{\Delta_5}) = 5$ of the K$3$
synthesis belongs to the Vol~III denominator normalisation. The BV
series here records the positive Fourier-degree coefficients through
$[\hbar_{\mathrm{BV}}^n]S^{\mathrm{eff}}$; it does not identify the
unweighted point $\hbar_{\mathrm{BV}}=1$ with the Lusztig
root-of-unity phase.
\end{remark}
