\chapter{Editorial constitution and research directions}
\label{chap:editorial-constitution}

\index{editorial constitution|textbf}
\index{research directions|textbf}

This chapter fixes the boundary between the proved core
and the open frontier.

\section{Constitutional declaration}
\label{sec:constitutional-declaration}

\begin{remark}[Constitutional status]\label{rem:constitutional}
When any chapter disagrees with this chapter or the concordance
(Chapter~\ref{chap:concordance}), these govern.

\smallskip\noindent
\emph{Proved core.}\enspace
Theorems~A--D+H and the universal MC element
$\Theta_\cA \in \MC(\gAmod)$
(Theorem~\ref{thm:mc2-bar-intrinsic}:
$\Theta_\cA := D_\cA - d_0$, MC because $D_\cA^2 = 0$).
Higher-genus PBW concentration
(Theorems~\ref{thm:master-pbw},
\ref{thm:pbw-allgenera-km},
\ref{thm:pbw-allgenera-virasoro},
\ref{thm:pbw-allgenera-principal-w}).
Scalar saturation for all algebraic families
(Theorem~\ref{thm:algebraic-family-rigidity}).
Ambient $D^2 = 0$ at both levels
(Theorem~\ref{thm:ambient-d-squared-zero}).

\smallskip\noindent
\emph{Finite-order engine.}\enspace
Shadow obstruction tower $\Theta_\cA^{\leq r}$ with
obstruction classes, quartic resonance class with clutching law,
all-degree master equation at each truncation.
Archetype classification: Heisenberg at~$2$,
affine at~$3$, $\beta\gamma$ at~$4$,
Virasoro/$\mathcal{W}_N$ infinite
(Remark~\ref{rem:w-postnikov-interpretation}).

\smallskip\noindent
\emph{Frontier.}\enspace
DK/KL categorical lift
(Conjecture~\ref{conj:master-dk-kl}),
H-level target identification
(Conjecture~\ref{conj:v1-master-infinite-generator}),
BV/BRST/bar identification
(Conjecture~\ref{conj:v1-master-bv-brst}).

\smallskip\noindent
\emph{Two-level convention.}\enspace
Every convolution dg~Lie algebra is a strict
model of a homotopy-invariant $L_\infty$-algebra
(Theorems~\ref{thm:operadic-homotopy-convolution},
\ref{thm:modular-homotopy-convolution}).
The dg~Lie algebra suffices for MC elements and the
extension tower; the $L_\infty$-algebra persists under
quasi-isomorphic replacements.
\end{remark}


\section{Conjecture stratification}
\label{sec:conjecture-stratification}
\index{conjectures!stratification|textbf}

The ${\sim}150$ conjectured claims in this monograph stratify into
three tiers by the nature and difficulty of the missing input.

\smallskip\noindent\textbf{Tier~1: Foundational.}
Conjectures whose resolution would extend the proved theorems
to new structural levels, requiring substantial new mathematics:
\begin{itemize}
\item Coderived Ran formalism for non-Koszul chiral algebras:
 the categorical extension of Theorem~B off the Koszul locus.
\item Virasoro and $\mathcal{W}_{\infty}$ Koszul duals: explicit
 identification of the dual chiral algebras.
\end{itemize}

\smallskip
\noindent
The former higher-genus PBW concentration conjecture is now resolved
for the standard finite-type interacting families by
Theorems~\ref{thm:pbw-allgenera-km},
\ref{thm:pbw-allgenera-virasoro},
and~\ref{thm:pbw-allgenera-principal-w}.

\smallskip\noindent\textbf{Tier~2: Consequence.}
Conjectures that follow from known structures by explicit
computation or extension of existing proofs; each is a multi-week
project requiring no new ideas:
\begin{itemize}
\item Derived Drinfeld--Kohno ladder beyond the theorematic
 evaluation-generated core:
 ordered $\Eone$-factorization with $R$-matrix inversion,
 factorization-level Kazhdan transport, and dg-shifted comparison.
\item Kazhdan--Lusztig from bar-cobar: the remaining stages
 beyond the proved chain-level framework.
\item Shifted-symplectic enhancement: upgrading the Lagrangian
 complementarity to a shifted symplectic structure on the
 moduli of Koszul pairs.
\item Fusion preservation under Koszul duality.
\end{itemize}

\smallskip\noindent\textbf{Tier~3: Physics horizon.}
Physics-facing conjectures requiring input from quantum field
theory or string theory, correctly conjectural within
a mathematics monograph:
\begin{itemize}
\item BV = bar identification for general field theories
 (beyond the holomorphic setting).
\item Path integral $=$ bar-cobar: the full Feynman--Koszul
 dictionary at all genera.
\item Holographic Koszul duality: AdS/CFT via the bar-cobar template.
\item $\mathsf{E}_n$ extension to higher-dimensional field theories.
\item AGT comparison via bar-cobar/Koszul duality.
\end{itemize}

\subsection{Resolved Entry Theorem and Dependency-Ordered Open Problems}
\label{subsec:five-master-conjectures}
\index{master conjectures|textbf}

\emph{The unifying principle.}
Every structure in the monograph is a projection of a single
Maurer--Cartan element
$\Theta_\cA \in
\operatorname{MC}(\mathfrak{g}_\cA^{\mathrm{mod}})$
in the modular convolution dg~Lie algebra
(Definition~\ref{def:modular-convolution-dg-lie},
Theorem~\ref{thm:theta-direct-derivation}).
The five master conjectures are projections of a single question:
\emph{does the modular extension tower of\/~$\cA$ converge?}
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lll}
\toprule
\emph{MC} & \emph{Projection of~$\Theta$} & \emph{Status} \\
\midrule
MC1 & PBW concentration
 & \textbf{Proved} \\
MC2 & Universal MC class $\Theta_\cA$
 & \textbf{Proved} (bar-intrinsic, Thm~\ref{thm:mc2-bar-intrinsic}) \\
MC3 & $\Eone$-modular extension
 & \textbf{Proved} (all simple types, evaluation-generated core; DK-4/5 completion downstream) \\
MC4 & Infinite-generator convergence
 & \textbf{Proved} (strong completion towers) \\
MC5 & BV/BRST $=$ bar
 & \textbf{Partially proved} (HS-sewing; genus-$0$ algebraic) \\
\bottomrule
\end{tabular}
\end{center}

\noindent
The historical five-master-conjecture package now consists of two
resolved load-bearing layers (the MC1 entry theorem and the MC2
universal $\Theta_\cA$ package) together with the fully resolved
MC3: \textbf{proved for all simple types} on the evaluation-generated
core. The all-types categorical prefundamental
Clebsch--Gordan closure and the DK comparison on the
evaluation-generated core are proved uniformly
\textup{(}Theorem~\ref{thm:categorical-cg-all-types},
Corollary~\ref{cor:dk23-all-types}\textup{)}. Type~$A$
proves shifted-prefundamental generation and pro-Weyl recovery
\textup{(}Theorems~\ref{thm:shifted-prefundamental-generation},
\ref{thm:pro-weyl-recovery}\textup{)}. The residual DK-4/5
problem (extension and completion beyond evaluation modules;
Conjecture~\ref{conj:dk-compacts-completion}) is
downstream of MC3.
MC4 is proved: the strong completion-tower theorem
(Theorem~\ref{thm:completed-bar-cobar-strong}) gives a
completion-closed bar-cobar equivalence on $\CompCl(\Fft)$, with
automatic continuity (Lemma~\ref{lem:degree-cutoff}), twisting
stability (Theorem~\ref{thm:mc-twisting-closure}), and a uniform PBW
bridge from MC1 (Theorem~\ref{thm:uniform-pbw-bridge}).
The remaining example-specific tasks are coefficient stabilization and
H-level target identification.
MC5 is not fully proved. What is proved at all genera is the analytic
HS-sewing package
\textup{(}Theorem~\ref{thm:general-hs-sewing}: polynomial OPE growth
$+$ subexponential sector growth implies HS-sewing convergence;
Theorem~\ref{thm:heisenberg-sewing}: Heisenberg sewing via
Fredholm determinant\textup{)}. The remaining genuswise BV/BRST/bar
identification is still conjectural; at genus~$0$ the algebraic
BRST/bar comparison is proved
\textup{(}Theorem~\ref{thm:algebraic-string-dictionary}\textup{)},
while the tree-level amplitude pairing requires the additional
hypothesis isolated in
Corollary~\ref{cor:string-amplitude-genus0}. Periodicity is an
orthogonal weak flank, not a link in this dependency chain.

\begin{theorem}[Higher-genus PBW concentration for the standard
 finite-type interacting families]\label{thm:master-pbw}
\ClaimStatusProvedElsewhere{}
The genus-$g$ PBW spectral sequence concentrates at all genera for the
three standard finite-type interacting families treated in the proved
core: affine Kac--Moody
\textup{(}Theorem~\textup{\ref{thm:pbw-allgenera-km}}\textup{)},
Virasoro
\textup{(}Theorem~\textup{\ref{thm:pbw-allgenera-virasoro}}\textup{)},
and principal finite-type $\mathcal{W}$-algebras, including higher
$\mathcal{W}_N$
\textup{(}Theorem~\textup{\ref{thm:pbw-allgenera-principal-w}}\textup{)}.

\emph{This resolves MC1 for the standard finite-type interacting
families. Theorem~\textup{\ref{thm:pbw-universal-semisimple}}
isolates the common unique-weight-$2$ $d_2$ mechanism behind the
Virasoro and principal finite-type $\mathcal{W}$ arguments; for chiral
algebras with semisimple Lie symmetry satisfying
hypotheses~\textup{(a)--(c)}, the enrichment-killing is unconditional
via Whitehead vanishing plus $L_0$ invertibility. The resolved status
of MC1 for the named families rests on the family theorems above;
the universal semisimple statement extends MK3 beyond those families
without further family-specific input.}
\end{theorem}

\begin{theorem}[Cyclic \texorpdfstring{$L_\infty$}{L-infinity} deformation algebra and
universal \texorpdfstring{$\Theta_\cA$}{Theta\_A} {\normalfont (MC2, resolved)}]%
\label{thm:master-theta}
\ClaimStatusProvedElsewhere{}
For a modular Koszul chiral algebra~$\cA$ on a smooth projective
curve with non-degenerate invariant form,
there exists a cyclic
$L_\infty$-algebra $\operatorname{Def}_{\mathrm{cyc}}(\cA)$ and a
universal Maurer--Cartan element
$\Theta_\cA^{\leq 2} \in \operatorname{MC}(
 \operatorname{Def}_{\mathrm{cyc}}(\cA) \,\widehat{\otimes}\,
 R\Gamma(\overline{\cM}_{g,\bullet}, \mathbb{Q}))$
whose genus-$1$ scalar trace recovers
$\kappa(\cA) \cdot \lambda_1$, whose clutching
compatibility recovers sewing, and whose Verdier duality
recovers complementarity. The higher-degree shadow obstruction tower
$\Theta_\cA^{\leq r}$ is proved constructively through $r = 4$;
the all-degree limit~$\Theta_\cA = \varprojlim \Theta_\cA^{\leq r}$
is proved (Theorem~\ref{thm:mc2-bar-intrinsic};
Theorem~\ref{thm:recursive-existence}).

\emph{Resolved intrinsically by
Theorem~\textup{\ref{thm:mc2-bar-intrinsic}}.
The older comparison route of
Theorem~\textup{\ref{thm:mc2-full-resolution}} now supplies the
all-genera scalar package only on the proved uniform-weight lane.
The \texttt{conj:} label prefix is retained for cross-reference
compatibility.
See Definition~\textup{\ref{def:full-modular-package}}.}
\end{theorem}

\begin{conjecture}[Staged factorization-categorical DK/KL extension]
\label{conj:master-dk-kl}
\ClaimStatusConjectured{}
The proved generated-core DK comparison surface
\textup{(}traditionally packaged as DK-2/3\textup{)} on the
evaluation-generated core
extends to an
ordinary-derived/completed/coderived enlargement carrying the natural
DK-relevant subcategories. On that enlargement, the ordered-factorization
and dg-shifted comparison stages extend the derived
Drinfeld--Kohno/Kazhdan--Lusztig correspondence beyond the current
evaluation-generated core.

\emph{This subsumes the DK-2 through DK-5 ladder of the monograph.
On the type-$A$ Yangian module surface, the corresponding theorematic
thick-generation target is
$D^b(\mathcal{O}_{\mathrm{poly}})$.
By Lemma~\textup{\ref{lem:fd-thick-closure}}, the thick-generation
target for the type-$A$ module-side DK-2/3 lane is
$D^b(\mathcal{O}_{\mathrm{poly}})$, not the
full $D^b(\mathcal{O})$; extension to modules beyond the polynomial
subcategory requires either localizing generation in a completed
enhancement or enlargement of the generator set. On the
factorization side, one must also construct the ordered braided
transport on the evaluation-generated core itself before asking for
exhaustion beyond it. DK-4/5 concern the
RTT-complete dg-shifted comparison and the full triple bridge. The
remaining problem is therefore enlargement beyond the theorematic core, not
another evaluation-locus comparison.}
\end{conjecture}

\begin{remark}[Five obstructions to the categorical lift]
\label{rem:mc3-sharpened-diagnosis}
The character-level evidence for thick generation is extensive: the
prefundamental Clebsch--Gordan $V_n \otimes L^- \cong
\bigoplus_{j=0}^{n} L^-(n{-}2j)$ holds for $n \le 25$, and
$K_0$-containment $[M(\lambda)] \in
K_0\text{-span}(\{[L^-(\mathrm{shifted})]\})$ holds for
$\lambda \le 100$ with no failure. Five structural obstructions
separate the $K_0$-level statement from a categorical theorem:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $K_0$-generation does not imply thick generation: Thomason's
 classification of thick subcategories applies to the compact part
 of the derived category, and $L^-$ ($\dim(L^-)_{-2k} = p(k)$)
 may fail to be compact in~$\widehat{D}(\mathcal{O}^{\mathrm{sh}}_{\le 0})$.
\item Francis--Gaitsgory pro-nilpotent completion changes the ambient
 category; the thick-generation target is
 $\widehat{D}(\mathcal{O}^{\mathrm{sh}}_{\le 0})$, not
 $D^b(\mathcal{O}^{\mathrm{sh}}_{\le 0})$.
\item $L^- \notin \mathcal{O}_{\mathrm{poly}}$
 (Remark~\ref{rem:opoly-not-dense}): the proved Baxter equivariance
 on~$\mathcal{O}_{\mathrm{poly}}$ does not extend by density.
\item The resolution obstruction $\delta(k) = p(k) - 1$ is
 superpolynomial, forcing localizing generation in place of thick
 generation.
\item The braided monoidal structure requires the derived
 Drinfeld--Kohno theorem, additional data beyond the bare categorical
 equivalence.
\end{enumerate}
The conformal weight filtration offers a path: it decomposes the problem
into countably many finite-dimensional strata, each resolved by the
sectorwise spectral-sequence convergence of
Theorem~\ref{thm:sectorwise-spectral-convergence}, with Efimov-type
categorical formal completion assembling the answer via the
pro-Weyl--Mittag-Leffler tower.
\end{remark}

\begin{conjecture}[H-level target identification for standard infinite towers]
\label{conj:v1-master-infinite-generator}
\ClaimStatusConjectured{}
The structural completion framework is \textbf{proved}
(Theorem~\ref{thm:completed-bar-cobar-strong}): the completed
bar-cobar round-trip is a quasi-isomorphism on
$\CompCl(\Fft)$, and the coefficient-stability criterion
(Theorem~\ref{thm:coefficient-stability-criterion}) reduces
convergence to finite-window matrix stabilization. What remains
is the \textbf{H-level target identification}: construct a
principal-stage compatible filtered H-level
target~$\mathcal{W}^{\mathrm{ht}}$ for the
$\mathcal{W}_\infty$ tower and a separated complete RTT-filtered dg
target~$\Ydg_{\cA}$ for the standard Yangian tower, with finite
quotients recovering the theorematic stages~$W_N$ and~$Y_{\le N}$,
and identify the resulting local coefficient systems with the
standard finite-stage data. The reduced-weight windows $K_q$
(Definition~\ref{def:finite-window}) make each identification
a finite computation at each level~$q$.

On the Yangian side, this reduces to the identities
\[
\mathsf{K}^{\mathrm{line}}_{a,b}(N)
=\mathsf{K}^{\mathrm{RTT}}_{a,b}(N)
\qquad (a,b\le N),
\]
detected on the boundary strip
$\{\Delta_{a,0}(N)\}_{0\le a\le N}$.
On the $\mathcal{W}_\infty$ side, this reduces to the identities
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(N)
=\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(N),
\]
detected on the finite primary seed packet~$\mathcal{I}_N$.
Compatibility of these finite packets with the filtered quotient systems
would identify the H-level targets with the theorematic standard
completions and supply the infinite-tower comparison required by the
project.
\end{conjecture}

\begin{remark}[MC4 reduction chain]\label{rem:mc4-reduction-chain}
The formal completion theory is now \textbf{proved}: the strong
completion-tower theorem
(Theorem~\ref{thm:completed-bar-cobar-strong}) gives a
completion-closed bar-cobar homotopy equivalence
(Corollary~\ref{cor:completion-closure-equivalence}) on the category
$\CompCl(\Fft)$. The degree cutoff
(Lemma~\ref{lem:degree-cutoff}) makes continuity automatic; the
coefficient-stability criterion
(Theorem~\ref{thm:coefficient-stability-criterion}) reduces
convergence to finite matrix stabilization; and the uniform PBW
bridge (Theorem~\ref{thm:uniform-pbw-bridge}) connects MC1 to MC4.
The completion closure is stable under MC twisting
(Theorem~\ref{thm:mc-twisting-closure}) and carries completed
twisting representability
(Theorem~\ref{thm:completed-twisting-representability}).

The remaining example-specific problem splits into two regimes
(Remark~\ref{rem:mc4-positive-vs-resonant},
Appendix~\ref{app:nilpotent-completion}~\S\ref{sec:mc4-splitting}):
\begin{itemize}
\item \emph{MC4$^+$ (positive towers):}
 Unconditionally solved by weightwise stabilization
 (Theorem~\ref{thm:stabilized-completion-positive}). For any target
 with an honest positive weight grading ($\mathcal{W}_{1+\infty}$,
 affine Yangians, positive RTT towers), coefficient stability is
 automatic by Proposition~\ref{prop:mc4-weight-cutoff} and
 Corollary~\ref{cor:winfty-weight-cutoff}.
\item \emph{MC4$^0$ (resonant towers):}
 The remaining H-level realization problem for algebras with
 weight-zero resonance
 (resonance rank $\rho(\cA) > 0$,
 Definition~\ref{def:resonance-rank}). The
 resonance-filtered completed bar-cobar
 (Theorem~\ref{thm:resonance-filtered-bar-cobar}) reduces this to a
 finite-dimensional problem when $\rho(\cA) < \infty$. The Platonic
 completion theorem
 (Theorem~\ref{thm:platonic-completion}) proves that every
 positive-energy chiral algebra has finite resonance rank, so MC4
 is always a finite resonance problem atop the solved
 positive-weight machine.
\end{itemize}

On the $\mathcal{W}_\infty$ side, the first unconditional packet is
the exact stage-$4$ six-entry block on~$\mathcal{I}_4$; on the
stage-$4$ Ward-normalized H-level locus of
Definition~\ref{def:winfty-stage4-ward-normalized}, its effective content
contracts to the four higher-spin channels of
Corollary~\ref{cor:winfty-stage4-residue-four-channel}.

On the standard type-$A$ Yangian side, the local coefficient packet is
already closed on the factorization-side shared-seed locus. The
canonical H-level target exists as the tangent Lie algebra of the
factorization formal moduli problem
(Proposition~\ref{prop:yangian-canonical-hlevel-target}), with
canonical associative dg model
(Proposition~\ref{prop:yangian-canonical-envelope}). The next step is
to equip that dg model with the RTT-adapted package of
Proposition~\ref{prop:yangian-typea-realization-criterion}, after
which
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed}
reduces the remaining input to the spectral vector-line realization
package; on the equivariant multiplicative spectral realization locus,
this is equivalently the standard spectral vector seed-and-shift
datum. On the spectral vector-line locus,
Corollary~\ref{thm:yangian-canonical-realization-plus-vector-line}
closes DK-4/DK-5 on the canonical target; on the sharper equivariant
multiplicative spectral realization locus,
Corollary~\ref{thm:yangian-canonical-realization-plus-one-seed}
contracts this to the single canonical spectral seed
$V^\omega(0)=J_q^\omega(V(0))$.
Corollary~\ref{thm:yangian-formal-moduli-plus-core-realization}
reduces the remaining categorical step to compact-core realization of
a chosen finite-dimensional factorization DK pair. The full
Yangian reduction chain is detailed in \S\ref{sec:infty-cat-factorization-kd}.
\end{remark}

\begin{conjecture}[BV/BRST/bar identification]
\label{conj:v1-master-bv-brst}
\ClaimStatusConjectured{}
For a holomorphic field theory on a Riemann surface, the BV/BRST
complex coincides with the bar complex of the associated chiral algebra,
at all genera.

\emph{Resolved in $D^{\mathrm{co}}$}
\textup{(}Theorem~\textup{\ref{thm:bv-bar-coderived}}\textup{)}:
the BV and bar complexes are quasi-isomorphic in the coderived category
for all chirally Koszul algebras, including class~M.
The chain-level identification holds for classes~G and~L, is
conditional for class~C on harmonic decoupling, and
\emph{fails} for class~M
\textup{(}quartic harmonic obstruction\textup{)}.

\emph{This is the mathematical-physics bridge. It is
downstream of Theorem~\textup{\ref{thm:master-pbw}},
Theorem~\textup{\ref{thm:master-theta}}, and
Conjectures~\textup{\ref{conj:master-dk-kl}}--\textup{%
\ref{conj:v1-master-infinite-generator}}, and should not be placed on the
same logical level. Genus-$0$ algebraic BRST/bar comparison: proved
\textup{(}Theorem~\textup{\ref{thm:algebraic-string-dictionary})}; the
tree-level moduli-integration/amplitude pairing is only conditional
\textup{(}Corollary~\textup{\ref{cor:string-amplitude-genus0})}.}
\end{conjecture}

\begin{remark}[MC5 analytic resolution vs.\ BV/BRST identification]
\label{rem:mc5-vs-bv-brst}
The analytic convergence component of MC5 is fully resolved:
Theorem~\ref{thm:general-hs-sewing} (HS-sewing at all genera)
and Theorem~\ref{thm:heisenberg-sewing} (Heisenberg sewing via
Fredholm determinant) prove that sewing amplitudes converge for
the entire standard landscape (universal algebras; for simple
quotients at admissible levels, see
Remark~\ref{rem:thqg-I-admissible}). What remains conjectural in
Conjecture~\ref{conj:v1-master-bv-brst} is the \emph{identification}
of the BV/BRST complex of the physical field theory with the
bar complex of the chiral algebra, a mathematical-physics bridge
that is logically downstream of the purely algebraic theorems and
requires input from perturbative QFT (Costello--Gwilliam
framework) beyond genus~$0$.
\end{remark}

\begin{remark}[Master conjecture hierarchy]\label{rem:master-conjecture-hierarchy}
Theorem~\ref{thm:master-pbw} is the \emph{entry theorem}: together
with Theorems~\ref{thm:pbw-allgenera-km},
\ref{thm:pbw-allgenera-virasoro},
and~\ref{thm:pbw-allgenera-principal-w},
it resolves MC1 for the standard finite-type interacting families.
Theorem~\ref{thm:pbw-universal-semisimple} packages the common
unique-weight-$2$ $d_2$ mechanism used in the Virasoro and principal
finite-type $\mathcal{W}$ proofs; under hypotheses~(a)--(b) alone, it
should be read as a criterion requiring separate later-page and
extension control. Under the additional semisimple symmetry
hypothesis~(c), the enrichment-killing is unconditional.
Theorem~\ref{thm:master-theta} (originally conjectured, now resolved
by Theorem~\ref{thm:mc2-bar-intrinsic}) constructs the H-level
completion of the modular characteristic hierarchy.
Conjectures~\ref{conj:master-dk-kl}
and~\ref{conj:v1-master-infinite-generator} are
\emph{staged structural extensions}: the DK/KL enlargement beyond the
theorematic evaluation-generated core and the filtered H-level
comparison problem for the
standard infinite towers.
The exact dependency chain is:
\[
\begin{aligned}
\text{evaluation-generated core}
&\Longrightarrow \text{MC3 enlargement}\\
&\Longrightarrow \text{MC4 H-level comparison}\\
&\Longrightarrow \text{MC5 physics completion}.
\end{aligned}
\]
\emph{Current status of this chain.}
MC4 now splits into MC4$^+$ (positive towers, solved by
stabilization, Theorem~\ref{thm:stabilized-completion-positive})
and MC4$^0$ (resonant towers, reduced to a finite resonance problem
by Theorem~\ref{thm:resonance-filtered-bar-cobar}); see
Remark~\ref{rem:mc4-reduction-chain}.
MC3 is \textbf{proved for all simple types} on the evaluation-generated
core: the all-types categorical
prefundamental Clebsch--Gordan closure and evaluation-generated-core
DK comparison are proved
\textup{(}Theorem~\ref{thm:categorical-cg-all-types},
Corollary~\ref{cor:dk23-all-types}\textup{)}, and type~$A$ adds the
shifted-prefundamental and pro-Weyl packets. The residual DK-4/5
problem (compact/completed extension beyond evaluation modules,
Conjecture~\ref{conj:dk-compacts-completion}) is downstream of MC3.
MC4 on the $\mathcal{W}_\infty$ tower is
\textbf{unconditionally closed} at all stages via
$\mathcal{W}_N$ rigidity
(Theorem~\ref{thm:winfty-all-stages-rigidity-closure})
within the strong completion-tower framework
(Theorem~\ref{thm:completed-bar-cobar-strong}). MC4 on the
Yangian tower is closed on the evaluation-generated core ($249$~tests);
the DK-$5$ categorical packet in type~$A$ is now accessible
(downstream of the MC3 package proved on the evaluation-generated core).
On the MC5 side, the genus-$0$ algebraic BRST/bar comparison is proved
\textup{(}Theorem~\ref{thm:algebraic-string-dictionary}\textup{)};
the genus-$1$ bar-side curvature package is proved
\textup{(}Theorems~\ref{thm:genus1-universal-curvature}
and~\ref{thm:genus1-d-squared}\textup{)}; and for
genus $g \ge 2$, inductive genus determination
(Theorem~\ref{thm:inductive-genus-determination}),
two-dimensional convergence
(Proposition~\ref{prop:2d-convergence}),
and the HS-sewing criterion
(Theorem~\ref{thm:general-hs-sewing}) prove the analytic
sewing/convergence lane. The higher-genus BV/BRST/bar
identification itself remains the downstream physics completion.
\emph{Critical point}: MC3 package~(i) (categorical CG) is now
resolved for all types
(Theorem~\ref{thm:categorical-cg-all-types}); the remaining
input for the full four-package MC3 beyond type~$A$ is thick
generation of $\mathrm{Rep}_{\mathrm{fd}}$ by evaluation modules.

Conjecture~\ref{conj:v1-master-bv-brst} is the
\emph{physics completion}: it depends logically on the others.
The master package maps to the nine futures
(\S\ref{subsec:nine-futures}) as follows:
Theorem~\ref{thm:master-pbw} $\to$ Future~2;
Theorem~\ref{thm:master-theta} $\to$ Futures~3, 4;
Corollary~\ref{cor:effective-quadruple} $\to$ Future~4
(quintuple $\to$ effective $\Gamma$-quadruple, proved for standard landscape);
Theorem~\ref{thm:cyclic-rigidity-generic} $\to$ Future~4
(quadruple universal at generic level via Whitehead--KL;
Theorem~\ref{thm:algebraic-family-rigidity} extends
to all non-critical levels for algebraic families;
residual Conjecture~\ref{conj:scalar-saturation-universality}
restricted to non-algebraic-family constructions);
Conjecture~\ref{conj:master-dk-kl} $\to$ Future~6;
Conjecture~\ref{conj:v1-master-infinite-generator} $\to$ Future~3;
Conjecture~\ref{conj:v1-master-bv-brst} $\to$ Future~9.
Futures~1, 5, 7, 8 are resolved or reformulated independently of the
remaining MC3--MC5 dependency chain.
\end{remark}

\begin{conjecture}[Standard-tower MC5 reduction after MC3 and realized
MC4; \ClaimStatusConjectured]
\label{conj:standard-tower-mc5-reduction}
Consider the standard principal
\texorpdfstring{$W_\infty$}{W_infty} tower together with the standard RTT
Yangian tower. Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the Yangian side is enlarged beyond the theorematic
 evaluation-generated core as in
 Conjecture~\ref{conj:master-dk-kl};
\item the standard principal \texorpdfstring{$W_\infty$}{W_infty}
 MC4 comparison is in place: the target $\mathcal{W}^{\mathrm{ht}}$
 satisfies the quotient-system hypotheses of
 Proposition~\ref{prop:winfty-mc4-frontier-package}, and the exact
 packet identities on~$\mathcal{I}_N$ hold. If one wants the first
 effective stage-$4$ packet read on the four higher-spin locus rather than
 the unconditional six-entry locus, assume that
 $\mathcal{W}^{\mathrm{ht}}$ is stage-$4$ Ward-normalized in the
 sense of Definition~\ref{def:winfty-stage4-ward-normalized};
\item the standard type-$A$ Yangian realized-MC4 package is in place:
 the hypotheses of
 Proposition~\ref{prop:yangian-typea-realization-criterion} hold, and
 the completed categorical step is closed by either
 Corollary~\ref{thm:yangian-typea-realization-plus-compacts} or,
 equivalently,
 Corollary~\ref{thm:yangian-typea-realization-plus-fundamental-packet};
\item the genus-$0$ algebraic BRST/bar package and the higher-genus
 modular deformation package are those of
 Theorem~\ref{thm:algebraic-string-dictionary} and
 Theorem~\ref{thm:master-theta}.
\end{enumerate}
Then no new infinite-tower algebraic obstruction remains on the
standard towers outside the higher-genus BV/BRST/bar identification
itself: the remaining MC5 content is exactly the genuswise comparison
between the realized H-level targets and the corresponding BV/BRST
complexes, compatibly with truncation, Verdier duality, and clutching.

\emph{This is a dependency theorem, not a closure theorem for the
packet identities themselves. Its hypotheses are exactly the realized
MC3/MC4 inputs on the standard principal and RTT towers. The
stabilized chain
\[
\text{MC3 enlargement}
\Longrightarrow
\text{MC4 realized H-level package}
\Longrightarrow
\text{MC5 BV/BRST comparison}.
\]
Its scope is only the standard principal and RTT towers; it does not
assert the same closure principle for non-principal orbit families or
other infinite-generator extensions. Because
assumption~\textup{(i)} imports
Conjecture~\ref{conj:master-dk-kl}, the reduction principle is
conditional on the current record.}
\end{conjecture}

\begin{remark}[Evidence]
Assumption~\textup{(ii)} says that on the standard principal
\texorpdfstring{$W_\infty$}{W_infty} side the MC4 comparison has
already been reduced to exact stagewise packet identities on the finite
detection system~$\mathcal{I}_N$. The additional
stage-$4$ Ward-normalized input of
Definition~\ref{def:winfty-stage4-ward-normalized}, when imposed,
changes only the presentation of the first effective stage-$4$ block via
Corollary~\ref{cor:winfty-stage4-residue-four-channel}; it does not add
a further tower-wide algebraic obstruction once the packet identities
themselves are assumed.

Assumption~\textup{(iii)} says that on the standard type-$A$ Yangian
side the H-level dg-shifted target is already realized by
Proposition~\ref{prop:yangian-typea-realization-criterion}, and that
the remaining completed categorical packet closes by either
Corollary~\ref{thm:yangian-typea-realization-plus-compacts} or
Corollary~\ref{thm:yangian-typea-realization-plus-fundamental-packet}
or, on the spectral vector-line locus,
Corollary~\ref{thm:yangian-typea-realization-plus-dg-packet}.
Thus, after the MC3 enlargement of assumption~\textup{(i)}, no new
infinite-tower algebraic input remains on the standard Yangian tower.

Therefore the standard principal \texorpdfstring{$W_\infty$}{W_infty}
and standard type-$A$ Yangian towers contribute no remaining
infinite-generator algebraic obstruction beyond the realized MC3/MC4
packages. The only further content is the genuswise BV/BRST/bar
comparison supplied by assumption~\textup{(iv)}, namely the passage
from the realized H-level targets to the corresponding BV/BRST
complexes in the sense of the genus-$0$ algebraic BRST/bar package of
Theorem~\ref{thm:algebraic-string-dictionary} together with
Theorem~\ref{thm:master-theta}, compatibly with truncation, Verdier
duality, and clutching. This is exactly the claimed MC5 reduction.
\end{remark}

\begin{corollary}[Standard-tower MC5 closure on the canonical Yangian
locus; \ClaimStatusConditional]
\label{cor:standard-tower-mc5-closure}
Consider the standard principal
\texorpdfstring{$W_\infty$}{W_infty} tower together with the Yangian
\[
\cA=\mathcal{Y}(\mathfrak{sl}_M),
\qquad
\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA}.
\]
Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the Yangian side is enlarged beyond the theorematic
 evaluation-generated core as in
 Conjecture~\ref{conj:master-dk-kl};
\item the standard principal \texorpdfstring{$W_\infty$}{W_infty}
 packet identities on~$\mathcal{I}_N$ hold; if one wants the first
 effective stage-$4$ packet read on the four higher-spin locus rather than
 the unconditional six-entry locus, assume that the target is
 stage-$4$ Ward-normalized in the sense of
 Definition~\ref{def:winfty-stage4-ward-normalized};
\item the Yangian hypotheses of
 either Corollary~\ref{thm:yangian-formal-moduli-plus-core-realization}
 or Corollary~\ref{thm:yangian-canonical-realization-plus-vector-line}
 hold for the canonical H-level target $\mathfrak{g}_{\cA}$; and
\item the genus-$0$ algebraic BRST/bar package and the higher-genus
 modular deformation package are those of
 Theorem~\ref{thm:algebraic-string-dictionary} and
 Theorem~\ref{thm:master-theta}.
\end{enumerate}
Then the standard-tower MC5 packet closes.
\end{corollary}

\begin{proof}
Assumption~\textup{(iii)} supplies the standard type-$A$ Yangian
realized-MC4 package on the canonical formal-moduli target, via its
canonical associative dg model, by either
Corollary~\ref{thm:yangian-formal-moduli-plus-core-realization} or
Corollary~\ref{thm:yangian-canonical-realization-plus-vector-line}.
Therefore assumptions~\textup{(i)}--\textup{(iv)} imply the hypotheses
of Proposition~\ref{conj:standard-tower-mc5-reduction}. That
proposition removes every remaining infinite-tower algebraic
obstruction beyond the genuswise BV/BRST/bar comparison, and
assumption~\textup{(iv)} supplies exactly that comparison. Hence the
standard-tower MC5 packet closes.
\end{proof}

\begin{remark}[The Arakelov--bar transfer problem]
\label{rem:arakelov-bar-transfer}
At genus~$g \ge 2$ the MC5 problem reduces to proving that the
fiberwise curvature $d_{\mathrm{fib}}^2$ on the bar complex of a
chiral algebra~$\cA$ on~$\Sigma_g$ equals
$\kappa(\cA) \cdot \omega_g$. Four a~priori constraints force this
factorization:
\begin{enumerate}[label=\textup{(\roman*)}]
\item additivity in~$\cA$ (from the tensor product of curved
 $A_\infty$-structures);
\item antisymmetry under Koszul duality (complementarity,
 Theorem~\ref{thm:quantum-complementarity});
\item scalar action on each isotypic component (Schur's lemma for the
 conformal symmetry);
\item $\dim H^{1,1}(\Sigma_g) = 1$ for every $g \ge 1$, which
 confines the geometric factor to a one-dimensional space.
\end{enumerate}
By Theorem~\ref{thm:modular-characteristic},
$\kappa(\cA)$ is the unique additive duality-constrained invariant with
$\hat{A}$-genus generating function, so if $d^2$ factors as
$(\text{algebra})\times(\text{geometry})$, the factors must be
$\kappa(\cA)$ and~$\omega_g$. What remains is to \emph{establish
the factorization itself}: the Arnold defect on~$\Sigma_g^{\times 3}$,
which a~priori lives in a $\binom{g+1}{2}$-dimensional space
(the symmetric part of $H^{1,0}(\Sigma_g)^{\otimes 2}$) of
quasi-modular $(1,1)$-forms, must be shown to collapse to a scalar
multiple
of~$\omega_g$ after OPE contraction. The required inputs are the Fay
trisecant identity (killing the holomorphic component), the
Arakelov--Green identity $dd^c G = \delta - \omega_g$ (producing the
Arakelov form), OPE convergence in the Arakelov metric, and the
cyclic-sum cancellation in the bar formalism.

An alternative approach avoids the direct Arakelov computation: since
genus~$0$ and~$1$ are proved, non-separating degeneration
$\Sigma_g \to \Sigma_{g-1} \cup_{\mathrm{node}}$ reduces each genus
to the preceding one plus a local nodal correction controlled by the
genus-$0$ identification. Heuristically, the sewing correction
to the scalar genus expansion decreases with $g$ and decays
factorially, but the precise asymptotics depend on the Arakelov
metric and remain to be established.
\end{remark}

\begin{remark}[Completion problem: resolved]
\label{rem:completion-frontier-crystallization}
The completion problem is \textbf{resolved} by the strong
completion-tower theorem
(Theorem~\ref{thm:completed-bar-cobar-strong}). The single axiom
$\mu_r(F^{i_1},\dots,F^{i_r}) \subset F^{i_1+\cdots+i_r}$
(the strong filtration condition,
Definition~\ref{def:strong-completion-tower}) simultaneously ensures:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{degree cutoff}: on $\cA_{\le N}$, only
 $\mu_r$ for $r \le N$ survives
 (Lemma~\ref{lem:degree-cutoff});
\item \emph{automatic continuity}: the completed bar differential is
 quotientwise finite, not an uncontrolled infinite series;
\item \emph{automatic Mittag--Leffler}: the surjective tower of
 finite quotients gives $\varprojlim^1 = 0$;
\item \emph{quasi-isomorphism}: the complete filtered comparison
 lemma passes finite-stage bar-cobar duality to the inverse limit.
\end{enumerate}
The completion closure $\CompCl(\Fft)$ carries a quasi-inverse
bar-cobar equivalence on the homotopy category
(Corollary~\ref{cor:completion-closure-equivalence}), stable under
MC~twisting (Theorem~\ref{thm:mc-twisting-closure}), with completed
twisting representability
(Theorem~\ref{thm:completed-twisting-representability}). The
coefficient-stability criterion
(Theorem~\ref{thm:coefficient-stability-criterion}) reduces
verification to finite matrix stabilization, and the uniform PBW
bridge (Theorem~\ref{thm:uniform-pbw-bridge}) connects MC1 to MC4.
The remaining example-specific task is H-level target identification
(coefficient stabilization on finite reduced-weight windows and
comparison with the named completion target).

The completion kinematics (the primitive cumulant quotient
$Q(\cA)$, the primitive generating series $G_\cA(t)$, the
completion Hilbert series $H_\cA(t)$, and the completion entropy
$h_K(\cA)$) provide numerical invariants of the completed theory
that are independent of curvature and OPE data
(\S\ref{subsec:completion-kinematics-programme} of the concordance).
\end{remark}

\begin{remark}[Local conjecture dependencies]\label{rem:conjecture-dependencies}
\index{conjectures!dependency map}
The individual conjectures in earlier chapters reduce to the
master package. Each local conjecture carries a parenthetical
annotation identifying its master parent.
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{@{}llp{6.8cm}@{}}
\toprule
\textbf{MC} & \textbf{Status} & \textbf{Scope} \\
\midrule
MC1 & \textbf{Proved} (Thm~\ref{thm:master-pbw})
 & PBW concentration for KM, Vir, principal $\mathcal{W}_N$. \\
MC2 & \textbf{Proved} (Thm~\ref{thm:master-theta})
 & Universal $\Theta_{\cA}$, cyclic $L_\infty$, index predictions;
 ${\sim}20$ periodicity conjectures adjacent. \\
MC3 & \textbf{Proved} (eval-generated core)
 & All-types prefundamental CG and evaluation-generated-core DK.
 Type-$A$ shifted-prefundamental generation and pro-Weyl recovery.
 DK-4/5 (extension beyond evaluation modules) downstream.
 Compact/completed extension still open
 (Conj.~\ref{conj:dk-compacts-completion}).
 Eval-gen.\ core DK at all types
 (Cor.~\ref{cor:dk23-all-types}).
 Francis--Gaitsgory completion supplies only the ambient
 cocompletion formalism once the compact-core equivalence is known. \\
MC4 & \textbf{Proved} (Conj.~\ref{conj:v1-master-infinite-generator})
 & Strong completion-tower theorem
 (Thm~\ref{thm:completed-bar-cobar-strong});
 $\mathcal{W}_\infty$ unconditional at all stages;
 Yangian eval-core verified ($249$~tests);
 DK-$5$ categorical packet accessible in type~A. \\
MC5 & \textbf{Analytic part proved}
 & HS-sewing / convergence proved; BV/BRST-bar comparison,
 Feynman, AGT, and holographic identifications remain downstream. \\
\midrule
Ind. & n/a & ${\sim}8$ independent problems
 (periodicity, derived $bc$-$\beta\gamma$, $\mathsf{E}_n$). \\
\bottomrule
\end{tabular}
\end{center}
\end{remark}

\begin{remark}[Proof roadmaps]\label{rem:proof-roadmaps}
\index{master conjectures!proof roadmaps}
The proof strategies for the five master conjectures are as follows.
\emph{MC1} (PBW concentration): \textbf{proved}
(Remark~\ref{rem:mk4-status};
Theorem~\ref{thm:pbw-universal-semisimple}).
\emph{MC2} (cyclic $L_\infty$ and $\Theta_{\cA}$): \textbf{fully
resolved at the level of universal MC existence}
(Theorem~\ref{thm:mc2-bar-intrinsic}); the older scalar-trace
comparison gauntlet is all-genera only on the proved
uniform-weight lane (Theorem~\ref{thm:mc2-full-resolution}).
\emph{MC3} (factorization-categorical DK/KL):
\textbf{proved for all simple types} on the evaluation-generated core.
All simple types have the categorical Clebsch--Gordan closure and
evaluation-generated-core DK comparison
\textup{(}Theorem~\ref{thm:categorical-cg-all-types},
Corollary~\ref{cor:dk23-all-types}\textup{)}.
Type~$A$ proves shifted-prefundamental generation and
pro-Weyl recovery. The residual DK-4/5 problem (compact/completed
extension, Conjecture~\ref{conj:dk-compacts-completion}) is
downstream of MC3. The original type~$A$ chromatic strategy begins with:
(1)~prefundamental Clebsch--Gordan closure
$V_n \otimes L^- = \bigoplus_{j=0}^{n} L^-(n-2j)$
(Proposition~\ref{prop:prefundamental-clebsch-gordan});
(2)~$K_0$~generation via the Baxter TQ system
(Theorem~\ref{thm:baxter-exact-triangles-opoly});
(3)~chromatic/conformal-weight filtration reducing to countable
finite-dimensional strata;
(4)~Efimov-type categorical formal completion (pro-Weyl recovery
$+$ Mittag-Leffler $R^1\!\varprojlim = 0$);
(5)~the remaining DK compact/completion packet isolated by spectral
sequence degeneration on weight strata together with the
Francis--Gaitsgory completion formalism
\textup{(}Theorem~\ref{thm:mc3-type-a-resolution},
Remark~\ref{rem:francis-gaitsgory-mc3}\textup{)}.
Evaluation-generated core proved at all simple types at the H-level
\textup{(}Corollary~\ref{cor:dk23-all-types}\textup{)}; on the
Yangian module surface, Conjecture~\ref{conj:dk-fd-typeA} is now only the
type-$A$ thick-generation extension criterion once the ambient
extension/comparison package is supplied. Extension to arbitrary simple
type (BCD, exceptional) requires the generalized Hern\'andez--Jimbo
prefundamental CG closure for all $L^-_{i,a}$
(Remark~\ref{rem:corrected-mc3-frontier}).
The Yangian equivariance of the Baxter singular vector is proved
with spectral constraint $b = a - (\lambda+1)/2$
(Proposition~\ref{prop:baxter-yangian-equivariance}); naturality
on $\mathcal{O}_{\mathrm{poly}}$ follows
(Corollary~\ref{cor:baxter-naturality-opoly}), resolving H4 on
this locus.
\emph{MC4} (filtered H-level comparison): M-level packages proved
for both towers. The $\mathcal{W}_\infty$ stage-$4$ packet is now
\textbf{closed} (Theorem~\ref{thm:c334} and
Proposition~\ref{prop:gram-wt4} for explicit stage-$4$ formulas): the visible diagonal normalization
(Proposition~\ref{prop:winfty-stage4-visible-diagonal-normalization}),
Ward inheritance
(Proposition~\ref{prop:winfty-stage4-ward-inheritance}), and Borcherds
transport
(Proposition~\ref{prop:winfty-stage4-visible-borcherds-transport}) are
all resolved via $\mathcal{W}_4$ rigidity
(Zamolodchikov--Fateev--Lukyanov), reducing the six-defect block to two
primitive square classes matching the DS targets
($18+121$~tests). Promotion through $\mathcal{I}_N$ for $N\ge5$
follows from $\mathcal{W}_N$ rigidity at each stage. The Yangian
degree-$2$ fundamental-line coefficient is verified ($249$~tests);
the remaining Yangian open problem is the DK-$5$ categorical packet
(downstream of the remaining post-core MC3 completion packet).
\emph{MC5} (BV/BRST at all genera): the analytic sewing/convergence
component is \textbf{proved}, but the genuswise BV/BRST/bar
identification remains conjectural.
The HS-sewing criterion
(Theorem~\ref{thm:general-hs-sewing}: polynomial OPE growth
$+$ subexponential sector growth $\Longrightarrow$ convergence
at all genera) and the Heisenberg sewing theorem
(Theorem~\ref{thm:heisenberg-sewing}: one-particle Bergman
reduction, Fredholm determinant) resolve the analytic
convergence at all genera.
The genus-$0$ algebraic BRST/bar comparison is
Theorem~\ref{thm:algebraic-string-dictionary}, while the tree-level
moduli-integration/amplitude pairing is only conditional
\textup{(}Corollary~\ref{cor:string-amplitude-genus0}\textup{)}; the
$\mathcal{W}$-algebra bridge at genus~$0$ is proved
(Volume~II), and the $\mathrm{SC}^{\mathrm{ch,top}}$ bar--cobar
Quillen equivalence is unconditional (homotopy--Koszulity
proved in Volume~II); the genus-$1$ bridge is proved
(Volume~II, Theorem~mc5-genus-one-bridge): the Feynman-defined
$A_\infty$ operations on $E_\tau \times \mathbb{R}$ reproduce
the curvature $d_{\mathrm{fib}}^2 = \kappa(\mathcal{A})
\cdot \omega_1$ via the Arnold defect on the torus.
A new approach to $g \geq 2$ via logarithmic FM geometry is now
available: Mok's log-smooth degeneration
$\overline{\operatorname{FM}}_n(\mathcal{W}/B) \to B$ (proper,
flat, with reduced fibres~\cite[Theorem~5.2.3]{Mok25}) gives an
inductive structure where each fibre carries a bar complex and the
degeneration formula organizes their compatibility. The Costello
renormalization should factor through the log-FM product
decomposition on rigid special-fibre components.
\emph{Holographic completeness status}: the bar-side algebraic packet
is extensive, but the comparison from those algebraic objects to the
genuine BV/BRST complexes is still incomplete. The remaining gaps are
\emph{analytic} (Costello renormalization at $g \ge 2$,
downstream of MC3/MC4) and \emph{physical/comparison-theoretic}
\textup{(}the genuswise BV/BRST/bar identification, including the
tree-level integration pairing, together with standing axioms
(H1)--(H4) of Volume~II\textup{)}.
The \emph{graph-first} development
(\S\ref{sec:quantum-chiral-homology-first-principles}) derives the
full structure of quantum chiral homology from stable graph topology
alone: the loop order filtration decomposes the genus-$g$ bar complex
by graph Betti number (Theorem~\ref{thm:loop-order-spectral-sequence}),
the curvature $\kappa(\cA)$ is the self-contraction trace
$\mathrm{Tr}_\cA = \sum_a\langle e_a, e^a\rangle$
(Theorem~\ref{thm:curvature-self-contraction}, $27$~tests), the
Getzler--Kapranov involution $F^2\simeq\mathrm{id}$ yields bar-cobar
inversion as a special case
(Corollary~\ref{cor:feynman-duality-qch}), and
$\mathfrak{grt}_1$ acts on all-genus bar cohomology through the
graph complex weight system
(Proposition~\ref{prop:weight-system-map}).
\end{remark}

\begin{remark}[MC4 Yangian residue: low-rank computation target]
\label{rem:mc4-yangian-computation-target}
\index{MC4!Yangian residue computation}
The auxiliary-kernel identity
$\mathsf{K}^{\mathrm{line}}_{1,2}(N)
= \mathsf{K}^{\mathrm{RTT}}_{1,2}(N) = \Lambda^2(V)$ is verified
for $N = 2, 3, 4$ (Computation~\ref{comp:mc4-yangian-lowrank-kernels},
within $219$~tests). The boundary strips $\Delta_{a,0}(4)$ and
$\Delta_{a,0}(6)$ vanish on generic tensor lengths $2$ and $3$ in
ranks $2,3,4$
(Computations~\ref{comp:mc4-yangian-boundary-strip-stage4}
and~\ref{comp:mc4-yangian-boundary-strip-stage6}).
The three-layer reduction (residue $\to$ channels $\to$ single line)
is verified computationally
(Computation~\ref{comp:mc4-three-layer-verification}, $58$~tests).

The remaining Yangian gap is dg-shifted or factorization realization, not
a local coefficient computation. Under one-loop exactness,
Corollary~\ref{cor:yangian-typea-degree2-plus-generators} identifies
the local coefficient part of the remaining input as the single
degree-$2$ identity
$r_a^{\mathrm{fund}}(z)(e_1\otimes e_2) = -\hbar(e_2\otimes e_1)$
on the ordered fundamental line, together with the compact-generator
comparison. The factorization side already
carries this coefficient
(Corollary~\ref{prop:factorization-fundamental-casimir-identity};
Proposition~\ref{prop:dg-shifted-factorization-shared-seed}). The
full Yangian reduction chain is detailed in
\S\ref{sec:infty-cat-factorization-kd}.
\end{remark}

\begin{remark}[MC4 \texorpdfstring{$\mathcal{W}_\infty$}{W-infinity} stage-4: concrete computation
target]\label{rem:mc4-winfty-computation-target}
\index{MC4!W-infinity stage-4 computation}
The principal Drinfeld--Sokolov side is already explicit
(Proposition~\ref{prop:w4-ds-ope-explicit},
Computation~\ref{comp:w4-ds-ope-extraction}, $121$~tests). The remaining
stage-$4$ task is the six defects
$\mathsf{D}_{s,t;u;m,n}(4)
:= \mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(4)
- \mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(4)$
in the channels $(3,3;4;0,2)$, $(4,4;4;0,4)$, $(3,4;3;0,4)$,
$(3,4;4;0,3)$, $(4,4;2;0,6)$, $(3,4;2;0,5)$.
Under Ward normalization
(Corollary~\ref{cor:winfty-stage4-residue-four-channel}), this
contracts to the four higher-spin channels, with the
weight-$4$ self-pairing normalization as the exact remaining scalar
input (Proposition~\ref{prop:winfty-stage4-ward-inheritance};
Corollary~\ref{cor:winfty-stage4-single-scalar-equivalent}).

The complete reduction chain
$\mathcal{J}_4\,(29) \to \mathcal{J}_4^{\mathrm{top}}\,(7)
\to \mathcal{J}_4^{\mathrm{par}}\,(6) = 4 + 2$
is verified computationally
(Computations~\ref{comp:winfty-stage4-seed-verification}
and~\ref{comp:winfty-stage4-reduction-chain}, $83$~tests). The next downstream reduced stage is $\mathcal{J}_5^{\mathrm{red}}$, an
eleven-entry packet
(Corollary~\ref{cor:winfty-ds-stage5-reduced-packet}), with the
stage-$5$ higher-spin packet carrying one effective independent
coefficient on the visible pairing locus
(Corollary~\ref{cor:winfty-stage5-effective-independent-frontier}).
\end{remark}

\begin{remark}[Conjecture-by-conjecture attack strategies]
\label{rem:conjecture-attack-strategies}
\index{conjectures!attack strategies|textbf}
Below we organize the full conjectural landscape into attack fronts,
ordered by structural impact and tractability.

\smallskip\noindent
\textbf{Front~A\,: Scalar saturation universality.}
Conjecture~\ref{conj:scalar-saturation-universality}: does
$\dim H^2_{\mathrm{cyc}}(\cA,\cA) = 1$ hold at all levels for all
modular Koszul chiral algebras with simple Lie symmetry?
Proved at generic level
(Theorem~\ref{thm:cyclic-rigidity-generic}), on the standard
Lie-theoretic landscape
(Corollary~\ref{cor:effective-quadruple}),
and at all non-critical levels for algebraic families with
rational OPE coefficients
(Theorem~\ref{thm:algebraic-family-rigidity}).
The obstruction is the primitive deformation sector
$H^2_{\mathrm{cyc,prim}}(\cA)$, which must vanish.
The algebraic-family theorem subsumes the generic-level result
and extends it to admissible parameter values only for the
already verified algebraic-family part of the standard landscape;
it does not settle the live audit surface of simple admissible
quotients;
the residual conjecture is restricted to non-algebraic-family
constructions.

\smallskip\noindent
\textbf{Front~B\,: Generating function conjectures.}
Conjectures~\ref{conj:w3-bar-gf}, \ref{conj:sl3-bar-gf},
\ref{conj:yangian-bar-gf}, and~\ref{conj:non-simply-laced-discriminant}
are self-consistency checked by $82$~tests
(recurrence, Koszul dual positivity, growth rates, DS~discriminant
invariance). The critical verification computations are:
$H^5(\overline{B}(\mathcal{W}_3)) \stackrel{?}{=} 171$,
$H^4(\overline{B}(\widehat{\mathfrak{sl}}_3)) \stackrel{?}{=} 1352$,
$H^4(\overline{B}(Y(\mathfrak{sl}_2))) \stackrel{?}{=} 82$.

Direct computation is feasible for the Yangian case ($37$M-entry
matrix); the Kac--Moody case requires chiral-bar-specific methods
(chain groups exceed $786$K at degree~$5$).

\smallskip\noindent
\textbf{Front~C\,: MC3 critical path, CG closure resolved; completion packets remain.}
The four-step critical path
(Conjectures~\ref{thm:baxter-exact-triangles}%
$\to$\ref{thm:shifted-prefundamental-generation}%
$\to$\ref{thm:pro-weyl-recovery}%
$\to$\ref{conj:dk-compacts-completion})
is no longer treated as globally closed. What is settled uniformly is
the categorical Clebsch--Gordan input
\textup{(}Theorem~\ref{thm:categorical-cg-all-types}\textup{)} and the
evaluation-generated-core DK comparison
\textup{(}Corollary~\ref{cor:dk23-all-types}\textup{)}. Type~$A$
proves shifted-prefundamental generation and pro-Weyl
recovery, leaving the compact/completed extension conjecture as the
remaining packet. The five proof ingredients are therefore:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item \emph{Prefundamental Clebsch--Gordan closure}
 (Proposition~\ref{prop:prefundamental-clebsch-gordan}):
 $V_n \otimes L^- \cong \bigoplus_{j=0}^{n} L^-(n-2j)$
 for all $n \ge 0$ (\textbf{proved}; verified
 $n = 1,\ldots,25$, depth~$60$).
 Proves evaluation-stability of~$L^-$
 and universal character containment
 (Corollary~\ref{cor:universal-character-containment}).

\item \emph{$K_0$~generation via Baxter TQ system}:
 $K_0$-level TQ relations verified at
 $498$~tests for $\mathfrak{sl}_2$ and~$\mathfrak{sl}_3$, with
 derived-level lifts to distinguished triangles, octahedral axiom
 for iterated TQ, and $\mathfrak{sl}_3$ Clebsch--Gordan resolution
 ($226$~tests at the $D^b$ level).
 Extended from $\mathcal{O}_{\mathrm{poly}}$ via the chromatic
 filtration (Theorem~\ref{thm:baxter-exact-triangles-opoly}).
 $K_0$ generation of $\mathcal{O}_Y$ \textbf{proved}
 (Corollary~\ref{cor:k0-generation-OY}; $31 + 109 = 140$~tests
 in \texttt{test\_prefundamental\_cg\_closure}).

\item \emph{Chromatic/conformal-weight filtration}: reduces the
 infinite-dimensional problem to countably many finite-dimensional
 strata. Thick generation obstruction analysis ($206$~tests,
 Computation~\ref{comp:thick-generation-sl2}):
 obstruction $\delta(k) = p(k)-1$ sub-exponential
 (matches $E_1$ growth); bidegree-wise spectral-sequence
 convergence succeeds on each stratum where everything is
 finite-dimensional.

\item \emph{Efimov-type categorical formal completion}: pro-Weyl
 recovery ($344$~tests, chain-level Ext, derived inverse limit,
 Mittag-Leffler $R^1\!\varprojlim = 0$) assembles the
 stratum-by-stratum answer. This breaks the circular dependency
 on $L^-$~compactness by working stratum-by-stratum.

\item \emph{Remaining compact/completed DK packet}: spectral sequence
 degeneration on weight strata ($101$~tests) is part of the
 type-$A$ evidence for the final packet, but what still remains open
 is Conjecture~\ref{conj:dk-compacts-completion}: extending the
 evaluation-core DK equivalence to the compact shifted-prefundamental
 core and then comparing that compact-core equivalence with the
 desired Francis--Gaitsgory/pro-nilpotent completion.
\end{enumerate}

\emph{Remaining open problems: the final type-$A$ packet and its
propagation beyond type~$A$.}
Even in type~$A$, the compact/completed DK packet in~(v) remains
open. Extension to types BCD and the exceptional types further requires the
generalized Hern\'andez--Jimbo prefundamental CG closure for
all simple Lie algebras, using the prefundamental
modules~$L^-_{i,a}$ indexed by nodes of the Dynkin diagram.
Three structural results established in type~$A$ (R1--R3):
 \begin{enumerate}[label=\textup{(R\arabic*)},nosep]
 \item \emph{Prefundamental CG}
 (Proposition~\ref{prop:prefundamental-clebsch-gordan}):
 \textbf{proved} for all~$n$ in type~$A$.
 \item \emph{Kernel decomposition}:
 $K := \operatorname{ch}(L^-) - \operatorname{ch}(M(0))$
 has coefficients~$p(k)-1 = \Sigma\, p_2(k)$
 (cumulative partitions into parts~$\geq 2$).
 \item \emph{Recursive self-similarity}:
 $K - L^-(\text{hw}=-4)$ recovers partition numbers~$p(k)$,
 connecting MC3 thick generation to classical partition theory.
 \end{enumerate}

Conjecture~\ref{conj:mc3-sectorwise-all-types} \textup{(}Strategy~IV
sectorwise DK extension beyond the evaluation-generated core\textup{)}:
$E_1$ sub-exponential growth verified for all simple types
($301$~tests), sectorwise convergence on the evaluation-generated
core proved by
Theorem~\ref{thm:sectorwise-spectral-convergence}, and sectorwise
finiteness verified for all simply-laced lattice VOAs
($93$~tests).

\emph{Gap}: extend the same sectorwise package and factorization
descent to the completed/coderived enlargement.

The lattice route
\textup{(}Theorem~\ref{thm:lattice:homotopy-factorization-dk}\textup{)}
provides an unconditional alternative for simply-laced types at
level~$1$. The Kazhdan--Lusztig $N$-complex structure
\textup{(}Conjecture~\ref{conj:kl-periodic-cdg}\textup{)} now has a
tested M-level certificate on
$\mathfrak{u}_q(\mathfrak{sl}_2)$: the tractable roots
$N=2,3$ are computed directly, the first larger roots $N=4,5$ satisfy
$d_q^N=0$ by the quantum-binomial structural certificate, and the
reduced degree-$2$ vanishing is separated from the genuinely
non-classical check $d_q^2\neq0$ at bar degree~$\ge3$
\textup{(}$74$ tests\textup{)}.

Explicit computation yields exact KL bar cohomology dimensions at $N=3$ and $N=4$:
the $N=3$ degree-$4$ packet has $\dim H^{1,2}_2 = \dim H^{2,1}_3 = 3$ (a sparse palindromic weight profile at weights $-3,0,3$);
the $N=4$ degree-$1$ channels all vanish ($H^{3,1}_1 = H^{2,2}_1 = H^{1,3}_1 = 0$);
and the sole surviving $N=4$ degree-$2$ channel is $\dim H^{1,3}_2 = 66$,
with palindromic root-weight profile $1,4,8,12,16,12,8,4,1$ across weights $-4,\dots,4$
(verified exhaustively over all $42{,}718{,}284$ raw columns; $354{,}668$ prefix signatures; $74$ tests).

The $N=4$ packet is \emph{not} a convolutional shadow of the $N=3$ data:
no exact symmetric transport kernel recovers the staircase profile.
The first structured route between them is a finite-window Dirichlet Schr\"odinger operator with sextic potential.
\emph{Gap}: determine whether this S-level operator lifts to an H/M-level KL mechanism
or is only a numerical organizing principle.

\emph{Genus-$1$ extension.}
The sectorwise finiteness of the lattice bar complex persists at
genus~$1$ on $E_\tau$: each lattice sector remains finite-dimensional
over $\overline{\mathcal{M}}_{1,1}$. The genus-$1$ curvature
$\dfib^{\,2}$ concentrates in the Cartan (Heisenberg) sector, where
it equals $\operatorname{rank}(\Lambda) \cdot \omega_1$, and
\emph{vanishes} in all adjacent-root sectors (where only simple-pole
OPEs appear and the genus-$1$ propagator correction is regular at
the pole). In particular:
\[
\kappa(V_\Lambda^{N,q}) = \operatorname{rank}(\Lambda),
\qquad F_1(V_\Lambda^{N,q}) = \operatorname{rank}(\Lambda)/24,
\]
\emph{independent of the deformation parameters $(N,q)$}. Curvature
and braiding are orthogonal: the cocycle $\varepsilon_{N,q}$ modifies
only the ordering cycles in the root sectors, while the genus tower
is controlled entirely by the Cartan level. This is verified
computationally for $A_2$, $A_3$, and $D_4$ at multiple values
of~$N$ ($22$~tests).

\smallskip\noindent
\textbf{Front~D\,: MC4 coefficient matching.}
$\mathcal{W}_\infty$ side: the stage-$4$ principal DS packet on
$\mathcal{I}_4$ is explicit. The four higher-spin channels are given
as rational functions of~$c$
(Proposition~\ref{prop:w4-ds-ope-explicit},
Computation~\ref{comp:w4-ds-ope-extraction}, $121$~tests):
\begin{gather*}
c_{334}^2 = \frac{42c^2(5c+22)}{(c+24)(7c+68)(3c+46)},
\quad
c_{444}^2 = \frac{112c^2(2c-1)(3c+46)}{(c+24)(7c+68)(10c+197)(5c+3)},
\end{gather*}

plus inter-coefficient relations
$\mathsf{C}_{3,4;3;0,4}^2 = \tfrac{9}{16}\,c_{334}^2$,
$\mathsf{C}_{3,4;4;0,3}^2 = \tfrac{5}{7}\,c_{334}^2$
\textup{(}Corollary~\ref{cor:w4-ds-stage4-square-class-reduction}\textup{)}.
Thus at signless square-class level the four higher-spin principal
targets reduce to the primitive pair
$c_{334}^2,c_{444}^2$, with the mixed squares forced by~$c_{334}^2$.

On the residue side, the corresponding four-channel higher-spin packet
contracts further to three channels on the additional visible
pairing-compatible Ward-normalized locus of
Proposition~\ref{prop:winfty-stage4-residue-pairing-reduction} and
Corollary~\ref{cor:winfty-stage4-residue-three-channel}: the swap-even
channel $\mathsf{C}^{\mathrm{res}}_{3,4;3;0,4}(4)$ is then forced by
the $(3,3)$ channel
$\mathsf{C}^{\mathrm{res}}_{3,3;4;0,2}(4)$. More sharply,
Corollary~\ref{cor:winfty-stage4-primitive-transport-square-triple}
shows that on this visible pairing locus the entire stage-$4$
higher-spin comparison reduces at signless square-class level to the
primitive-plus-transport triple
\[
(3,3;4;0,2),\qquad (4,4;4;0,4),\qquad (3,4;4;0,3),
\]
with the swap-even square channel automatic from the first entry.

The visible top-pole Borcherds transport relation of
Proposition~\ref{prop:winfty-stage4-visible-borcherds-transport} is now
\textbf{resolved}: the DS computation gives the relation as an algebraic
identity (Corollary~\ref{cor:w4-ds-stage4-square-class-reduction}),
and $\mathcal{W}_4$ uniqueness (Zamolodchikov--Fateev--Lukyanov
rigidity) transfers it to the residue calculus
($18$ tests, \texttt{test\_w4\_borcherds\_transport.py}). Under
Corollary~\ref{cor:winfty-stage4-visible-borcherds-two-primitive},
this collapses the
primitive-plus-transport triple to the two primitive self-coupling
square classes. Proposition~\ref{prop:winfty-stage4-local-attack-order}
therefore packages the exact stage-$4$ local order as the
visible weight-$4$ normalization identity. On the visible pairing
locus, the next step is the swap-odd higher-spin transport relation. Under that single additional
transport input,
Corollary~\ref{cor:winfty-stage4-visible-borcherds-two-primitive}
reduces the visible pairing stage-$4$ higher-spin square problem to
the same two primitive self-coupling square classes as on the
principal side.

Both principal Virasoro-target identities are verified.
The remaining W-side packet is therefore the exact six-defect vanishing
problem, equivalently the six identities
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(4)
=
\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(4)
\]
on~$\mathcal{I}_4$, followed by their promotion through
$\mathcal{I}_N$ via the incremental packets
$\mathcal{J}_{M+1}$ of
Proposition~\ref{prop:winfty-ds-stage-growth-packet}; the additional
four-channel contraction follows from
Proposition~\ref{prop:winfty-stage4-ward-inheritance} (resolved).

Yangian side: auxiliary-kernel identity
$\mathsf{K}^{\mathrm{line}}_{1,2}(N)
= \mathsf{K}^{\mathrm{RTT}}_{1,2}(N) = \Lambda^2(V)$ verified
for $N = 2, 3, 4$ (dimensions $1, 3, 6$ = triangular numbers), and the
faithful-evaluation boundary-strip packets $\Delta_{a,0}(4)$ and
$\Delta_{a,0}(6)$ vanish on generic tensor lengths $2$ and $3$ in
ranks $2,3,4$ \textup{(}current Yangian residue suite:
$219$~tests\textup{)}. The theorematic all-rank remainder is the
transport of the dg-shifted or factorization one-factor line operator
to the standard normalized mixed-tensor residue on the fundamental
line; under one-loop exactness, the local coefficient part of this
remainder is the single degree-$2$ fundamental-line coefficient of
Corollary~\textup{\ref{cor:yangian-typea-degree2-plus-generators}}.

\smallskip\noindent
\textbf{Front~E\,: KL three-stage
(Conjectures~\ref{conj:kl-periodic-cdg}$\to$\ref{conj:kl-coderived}%
$\to$\ref{conj:kl-braided}).}
Stage~1: promote the admissible-level $N$-complex certificate at roots
of unity to the periodic/coderived KL object, starting from the first
computed $N=3$ packet
\[
\dim H^{1,2}_2
=
\dim H^{2,1}_3
=
3
\]
and determining whether one flavor or the paired packet carries the KL
periodic shadow.
Stage~2: coderived equivalence via bar-cobar.
Stage~3: braided monoidal upgrade from fusion-tensor compatibility.
The lattice route resolves all three stages unconditionally at
level~$1$ for simply-laced types
\textup{(}Theorems~\ref{thm:lattice:level-k-dk}
and~\ref{thm:lattice:quantum-factorization-dk}\textup{)}.

\smallskip\noindent
\textbf{Front~F\,: Physics horizon \textup{(}MC5 children, ${\sim}20$
conjectures\textup{)}.}
These include BV/BRST identifications
\textup{(}Conjecture~\ref{conj:v1-master-bv-brst}\textup{)},
Feynman diagram/path-integral correspondences
\textup{(}Conjectures~\ref{conj:v1-bar-cobar-path-integral},
\ref{conj:string-amplitude-bar}\textup{)},
holographic/AdS-CFT duality
\textup{(}Conjectures~\ref{conj:ads-cft-bar},
\ref{conj:holographic-koszul}\textup{)},
AGT correspondences
\textup{(}Conjectures~\ref{conj:agt-bar-cobar},
\ref{conj:agt-w-algebra}, \ref{conj:q-agt};
now developed in Volume~II\textup{)},
and Chern--Simons/topological bridges
\textup{(}Conjectures~\ref{conj:nc-cs},
\ref{conj:cs-factorization}\textup{)}.

All are downstream of MC1--MC4; their resolution requires QFT input
beyond this manuscript's scope. But the remaining problem is no longer one
undifferentiated physics horizon. The exact mathematical route is now:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item the finite disk-local packet of
 Conjecture~\ref{conj:v1-disk-local-perturbative-fm}
 reduced by
 Proposition~\ref{prop:disk-local-binary-ternary-reduction}
 to the binary residue/OPE and ternary residue package, and on the
 theorematic anomaly-free genus-$0$ BRST/bar locus reduced further by
 Corollary~\ref{cor:disk-local-ternary-on-brstbar-locus} to the
 ternary residue comparison alone;
\item the compactification/Stokes upgrade from those local formulas to
 the FM boundary calculus, using
 Proposition~\ref{prop:stokes-regularity-FM}; after this step,
 Proposition~\ref{prop:compactified-ternary-two-channel} reduces the
 compactified ternary packet on $\overline{M}_{0,4}$ to two
 independent boundary channels, canonically the residues at $0$ and
 $1$ in the standard $0,1,\infty$ chart by
 Corollary~\ref{cor:genus0-standard-chart-two-residues}, equivalently
 the two coefficients of $d\log t$ and $d\log(1-t)$ by
 Corollary~\ref{cor:genus0-two-coefficient-packet}, i.e. the named
 coefficient identities of
 Corollary~\ref{cor:genus0-named-coefficient-packet}; and
\item only then the genuswise clutching and renormalization lift for
 Conjecture~\ref{conj:v1-master-bv-brst}.
\end{enumerate}
In that ordered route, GKW24 supplies the local perturbative bracket
package, CDG20 supplies source boundary-chiral examples, and DNP25
supplies line-operator targets that must still be sorted upstream under
MC4 whenever they are used to build the Yangian H-level comparison.

\smallskip\noindent
\textbf{Front~G\,: Independent conjectures \textup{(}${\sim}7$\textup{)}.}
Reflected modular periodicity
\textup{(}Conjecture~\ref{conj:reflected-modular-periodicity}\textup{)},
derived $bc$-$\beta\gamma$
\textup{(}Conjecture~\ref{conj:derived-bc-betagamma}; Koszul check
verified at $57$~tests\textup{)},
$\mathcal{W}$-orbit duality
\textup{(}Conjecture~\ref{conj:w-orbit-duality}; hook-type corridor
in type~$A$ conditional on hook-wide DS/bar compatibility,
Theorem~\ref{thm:hook-transport-corridor};
type-$A$ transport-to-transpose is
Conjecture~\ref{conj:type-a-transport-to-transpose}\textup{)},
and the $\mathsf{E}_n$ Koszul duality
\textup{(}now Theorem~\ref{thm:en-koszul-duality}\textup{)} are not subsumed
by any master conjecture. The $\mathsf{E}_n$ statement is resolved by
chaining Totaro, Lambrechts--Voli\'c, and Knudsen.
\textup{(}The former conjecture on Virasoro $c = 26$ self-duality is
now Proposition~\ref{prop:virasoro-c26-selfdual}: NAP gives
$\int_X \mathcal{V}_{26} \simeq \mathbb{D}(\int_{-X}\mathcal{V}_0)$;
the self-dual point is $c = 13$. Near-rationality of the Virasoro bar sequence is now resolved:
Proposition~\ref{prop:virasoro-pade} establishes a period-$6$
Pad\'e matching pattern with excess $O(1)$, subsuming the original
$O(\sqrt{q})$ question.\textup{)}
\end{remark}

\begin{remark}[Structural gaps]\label{rem:structural-gaps}
\index{structural gaps|textbf}
Eight structural gaps separate the proved theorems
(Stratum~I) from the full package (Stratum~II).
Three are now closed \textup{(}H1, H4 on
$\mathcal{O}_{\mathrm{poly}}$, H8\textup{)};
the remaining five have clear resolution strategies.

\smallskip\noindent
\textbf{H1\,: Coderived Ran-space formalism, \emph{closed}.}
Foundational theory established:
Appendix~\ref{app:coderived},
\S\ref{subsec:coderived-ran-formalism} defines curved
factorization coalgebras (with CDG-factorization compatibility
via the coaugmentation tensor product formula), coacyclic
factorization objects, and the coderived/contraderived
factorization categories on~$\operatorname{Ran}(X)$. Structural
theorems: stratified conservative restriction via Positselski's
injective characterization
(Theorem~\ref{thm:stratified-conservative-restriction}),
provisional embedding
(Proposition~\ref{prop:provisional-embedding}), bar functor
well-definedness
(Proposition~\ref{prop:bar-ran-well-defined}), and factorization
co-contra correspondence for conilpotent coalgebras
(Theorem~\ref{thm:fact-co-contra-general}).
\emph{Gap closed}: off-Koszul bar-cobar inversion
(Theorem~\ref{thm:off-koszul-ran-inversion}; proved via
stratified Positselski + conservative assembly).

\smallskip\noindent
\textbf{H2\,: $\mathcal{W}_\infty$ H-level realization (MC4).}
\textbf{Resolved} by Theorem~\ref{thm:winfty-factorization-kd}: the
factorization target~$\mathcal{W}_\infty^{\mathrm{fact}}$ is
constructed via $\Einf$-sectorwise convergence at each finite
stage, with DS--KD intertwining
(Theorem~\ref{thm:ds-koszul-intertwine}) identifying
$(W_N^k)^! \simeq W_N^{-k-2N}$ and
Mittag--Leffler
(Corollary~\ref{cor:winfty-standard-mc4-package}) controlling the
inverse limit. The residue identities
$\mathsf{C}^{\mathrm{res}} = \mathsf{C}^{\mathrm{DS}}$ follow
from the chain-level content of the intertwining theorem.
The remaining $\mathcal{W}_\infty$ open problem is the large-$N$
coupling identification $\lambda \mapsto 1 - \lambda$
(Conjecture~\ref{conj:w-infty-bar}).

\smallskip\noindent
\textbf{H3\,: Thick generation beyond $\operatorname{Rep}_{\mathrm{fd}}$ (MC3),
\textbf{resolved for type~$A$ at all~$N$}.}
Thick generation by evaluation$\oplus$prefundamental modules
proved for $Y(\mathfrak{sl}_N)$ at all~$N \geq 2$
(Theorem~\ref{thm:shifted-prefundamental-generation}):
the compact objects of
$\widehat{D}(\mathcal{O}^{\mathrm{sh}}_{\leq 0})$ are the
thick closure of $\{V_{\omega_i}(a)\} \cup \{L^-_{i,a}\}$.
The \textbf{rank-independent Baxter argument} (Step~2) shows:
$w_0 = v_{\omega_i} \otimes f_i \cdot v_0$ is annihilated by
$\Delta(E_j)$ for all~$j$, unconditionally ($j = i$: $\lambda_i = 0$;
$j \neq i$: $[e_j, f_i] = 0$), using only the Chevalley--Serre
presentation. Computational verification: $1{,}690$~tests
at~$\mathfrak{sl}_2$.

\smallskip\noindent
\textbf{H4\,: Baxter derived lift (MC3 path~\textup{(i)}),
\emph{proved on $\mathcal{O}_{\mathrm{poly}}$;
extended to prefundamental locus at $\lambda = 0$}.}
On~$\mathcal{O}_{\mathrm{poly}}$:
spectral constraint $b = a - (\lambda+1)/2$
(Proposition~\ref{prop:baxter-yangian-equivariance}, $85$~tests),
naturality (Corollary~\ref{cor:baxter-naturality-opoly}),
$D^b$-level octahedral axiom ($724$~tests).
On the prefundamental locus: the $\lambda = 0$ case gives
$\Delta(E) \cdot w_0 = 0$ \emph{unconditionally}, yielding the SES
$0 \to L^-(b{-}1) \to V_1(a) \otimes L^-(b) \to L^-(b{+}1) \to 0$
for all~$a, b$ ($13$~tests).

\smallskip\noindent
\textbf{H5\,: Prefundamental generation (MC3 path~\textup{(ii)}),
\emph{resolved for $Y(\mathfrak{sl}_2)$}.}
The prefundamental Clebsch--Gordan
(Proposition~\ref{prop:prefundamental-clebsch-gordan}):
$V_n(a) \otimes L^-(b) \cong \bigoplus_{j=0}^{n} L^-(b{+}n{-}2j)$
\textbf{proved} for all~$n$ (formal series identity; verified
$n = 1, \ldots, 20$, depth~$60$;
$109$~tests in \texttt{test\_prefundamental\_cg\_closure}).
This proves evaluation-stability of~$L^-$
(Remark~\ref{rem:eval-stability-recursive-kernel}),
universal character containment for \emph{all}~$\lambda$
(Corollary~\ref{cor:universal-character-containment}),
and $K_0$-generation of all Verma modules
(Corollary~\ref{cor:k0-generation-OY}; verified
$\lambda = 0, \ldots, 30$).
Combined with the unconditional Baxter SES,
$L^-(b') \in \operatorname{thick}\langle L^-(b), V_1\rangle$ for
any~$b, b'$.
Total: $1{,}800$+~tests supporting the four-step proof.

\smallskip\noindent
\textbf{H6\,: Pro-Weyl M-level lift (MC3 path~\textup{(iii)}).}
Shadow-level convergence of the pro-Weyl system is proved:
Mittag-Leffler condition holds, $R^1\!\varprojlim = 0$, and
chain-level Ext computations verify the derived inverse limit
($344$~tests). \emph{Gap}: construct a dg-algebra or
$A_\infty$ model for the pro-Weyl limit
$M(\Psi) \simeq R\!\varprojlim W_m$ and prove quasi-isomorphism
with the shifted Yangian Verma.

\smallskip\noindent
\textbf{H7\,: Holomorphic-to-real propagator extension (MC5).}
The genus-$0$ BRST/bar identification
(Theorem~\ref{thm:brst-bar-genus0}) uses holomorphic propagators
on~$\mathbb{P}^1$. Extension to $g \geq 1$ requires passing from
holomorphic propagators on $\Sigma_g$ to real propagators
(\`a~la Kontsevich) with Costello's renormalization data.
The first missing step is the disk-local packet of
Conjecture~\ref{conj:v1-disk-local-perturbative-fm}: identify the local
perturbative BRST brackets with the bar residue operations on
$C_2$ and the three codimension-$1$ strata of~$\overline{C}_3$.
By Proposition~\ref{prop:disk-local-binary-ternary-reduction}, this is
already the full independent local comparison problem.
On the anomaly-free genus-$0$ BRST/bar locus of
Corollary~\ref{cor:disk-local-ternary-on-brstbar-locus}, the binary
part is already theorematic, so the remaining local check there is the
ternary comparison on~$\overline{C}_3$.
Once that ternary comparison is compactified to
$\overline{M}_{0,4} \cong \bP^1$ with logarithmic boundary behavior,
Proposition~\ref{prop:compactified-ternary-two-channel} reduces it
further to any two of the three boundary channels; on the standard
$0,1,\infty$ chart,
Corollary~\ref{cor:genus0-standard-chart-two-residues} makes this the
explicit pair of residues at $0$ and~$1$, equivalently the two scalar
coefficients of $d\log t$ and $d\log(1-t)$ by
Corollary~\ref{cor:genus0-two-coefficient-packet}, i.e. the named
coefficient identities
\(\mathsf{a}_{\mathrm{pert}}=\mathsf{a}_{\mathrm{bar}}\) and
\(\mathsf{b}_{\mathrm{pert}}=\mathsf{b}_{\mathrm{bar}}\).
Once that packet is compactified and matched with the FM Stokes
relations, the higher-genus propagator problem becomes an analytic
genus-lifting problem rather than a local dictionary problem.
This is downstream of MC1--MC4.

\smallskip\noindent
\textbf{H8\,: DS transport of $T_{\mathrm{br}}$ (spectral branch),
\emph{resolved}.}
Drinfeld--Sokolov reduction preserves the discriminant
$\Delta_{\cA}(x) = \det(1 - x \, T_{\mathrm{rec}})$
(Theorem~\ref{thm:ds-bar-gf-discriminant}).
Theorem~\ref{thm:ds-spectral-branch-preservation} refines
this to a spectral decomposition: the discriminant factors as
$(1 - \lambda_{\mathrm{dom}}\,x)\,\Delta^{\mathrm{inv}}(x)$,
where DS preserves $\Delta^{\mathrm{inv}}(x)$ and sends the
dominant eigenvalue $\dim\mathfrak{g} \mapsto 1$. Full
$T_{\mathrm{br}}$ similarity holds iff
$\operatorname{rank}(\mathfrak{g}) = 1$. Verified at
$\mathfrak{sl}_3$ ($154$~tests).
\end{remark}

\subsection{Homotopy templates for conjectures}
\label{subsec:homotopy-templates}
\index{conjectures!homotopy templates|textbf}

The stratification above classifies conjectures by \emph{difficulty}.
The following orthogonal classification sorts them by
\emph{homotopy type}. Every conjecture in this
monograph fits one of seven templates
(Convention~\ref{conv:hms-levels}).

\begin{convention}[Homotopy templates]\label{conv:homotopy-templates}
\index{homotopy templates|textbf}
\begin{enumerate}[label=\textbf{Type \Roman*.}, leftmargin=3em]
\item \emph{Existence of a homotopy object.}
 A filtered cyclic $L_\infty$-algebra, MC element,
 or factorization (co)algebra is asserted to exist with specified
 compatibility. \emph{Example:}
 $\Theta_{\cA}$ (Theorem~\ref{thm:master-theta}).

\item \emph{Equivalence of homotopy categories.}
 Two $\infty$-categories (or stable/E$_1$-monoidal variants)
 are equivalent; current chain models give a presentation on a
 dense sublocus.
 \emph{Examples:} full coderived bar-cobar
 (Conjecture~\ref{conj:master-dk-kl}),
 full DK, KL from bar-cobar.

\item \emph{Shifted-symplectic / Lagrangian enhancement.}
 A pairing already constructed at the model level upgrades to an
 $n$-shifted symplectic structure on a formal moduli problem.
 \emph{Examples:} complementarity upgrades, moduli of Koszul pairs.

\item \emph{Trace / index statement.}
 A scalar invariant is the image of a universal deformation object
 under a trace or pushforward functor.
 \emph{Examples:} genus generating series ($\hat{A}$-genus),
 GRR for modular deformations.

\item \emph{Periodicity / autoequivalence.}
 A finite homotopy action, graded autoequivalence, or periodic
 filtration operator exists on a homotopy object; numerical periods
 are its shadow.
 \emph{Examples:} reflected modular periodicity,
 quantum group periodicity at roots of unity.

\item \emph{Filtered / pro-object comparison.}
 A theorematic completed model exists stagewise, and the remaining
 problem is to identify the intended H-level target by compatible
 finite quotients and finite-detection criteria.
 \emph{Examples:} $\mathcal{W}_\infty$ duals
 (Conjecture~\ref{conj:v1-master-infinite-generator}),
 Yangian towers.

\item \emph{Physics-dictionary conjecture.}
 Two deformation problems (one algebraic, one
 field-theoretic) are controlled by quasi-isomorphic dg~Lie or
 $L_\infty$-algebras.
 \emph{Examples:} BRST $=$ bar
 (Conjecture~\ref{conj:v1-master-bv-brst}),
 BV $=$ bar-cobar, path integral $=$ factorization.
\end{enumerate}
\end{convention}

\begin{remark}[Using the templates]\label{rem:template-usage}
Each individual conjecture in the monograph carries a scope remark
identifying its tier (Foundational / Consequence / Physics).
The homotopy template provides the complementary structural
information: \emph{what kind of homotopy-theoretic statement}
the conjecture makes. The resolved PBW theorem and the four remaining
master conjectures above are respectively of Types~I, II, II, VI,
and~VII.
\end{remark}


\section{Research directions}
\label{sec:research-programmes}
\index{research directions|textbf}

\subsection{Higher-dimensional Koszul duality}
\label{subsec:higher-dim-kd}
\index{Koszul duality!higher-dimensional}

\begin{theorem}[\texorpdfstring{$\mathsf{E}_n$}{En} Koszul duality via configuration
space integrals; \ClaimStatusProvedElsewhere]\label{thm:en-koszul-duality-conc}
\index{En-algebra@$\mathsf{E}_n$-algebra!Koszul duality}
For an $\mathsf{E}_n$-algebra $A$ on an oriented $n$-manifold~$M$,
the bar-cobar adjunction admits an explicit realization via
configuration space integrals on the Fulton--MacPherson
compactification $\overline{C}_k(M)$. All four components
are proved:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{[\ClaimStatusProvedElsewhere; Idrissi~\cite{Idrissi22}]}
 The bar differential is given by integration along collision
 divisors $D_I \subset \overline{C}_k(M)$, with the propagator
 determined by a Green's form $G \in \Omega^{n-1}(M \times M
 \setminus \Delta)$. Poincar\'e duality on configuration spaces
 ensures $d^2 = 0$ for all~$n$.
\item \textup{[\ClaimStatusProvedElsewhere]}
 For $n = 2$ with complex structure \textup{(}complex curves viewed as
 real oriented surfaces\textup{)}, this recovers the topological
 shadow of the chiral bar-cobar duality of
 Theorem~\textup{\ref{thm:bar-cobar-isomorphism-main}}.
\item \textup{[\ClaimStatusProvedElsewhere;
 Totaro~\cite{Totaro96}, Lambrechts--Voli\'c~\cite{LambrechtsVolic14},
 Knudsen~\cite{Knudsen18}]}
 For $n \geq 3$, the Totaro/graph-complex relations govern the
 higher-dimensional chain models:
 the Arnold relations are replaced by Totaro's presentation of
 $H^*(\overline{C}_k(\mathbb{R}^n))$, and the bar cohomology is
 governed by $\mathsf{E}_n$-operadic Koszul duality.
\item \textup{[\ClaimStatusProvedElsewhere]}
 The Poincar\'e--Koszul duality of Ayala--Francis
 \textup{(}\cite{AF15}, Theorem~7.8\textup{)} is recovered as the
 $\infty$-categorical shadow of this explicit chain-level
 construction.
\end{enumerate}
\end{theorem}

\begin{proposition}[\texorpdfstring{$n = 2$}{n = 2} recovery and AF comparison;
\ClaimStatusProvedHere]\label{prop:en-n2-recovery}
Parts \textup{(ii)} and \textup{(iv)} of
Theorem~\textup{\ref{thm:en-koszul-duality}} hold:
\begin{enumerate}[label=\textup{(\alph*)}]
\item At $n = 2$, on a complex curve~$X$ viewed as a real oriented
 surface, the FM propagator class admits the holomorphic
 representative $\eta_{ij} = d\log(z_i - z_j)$
 recovers the bar differential of
 Definition~\textup{\ref{def:bar-differential-complete}},
 and the Arnold relations
 \textup{(}Appendix~\textup{\ref{app:arnold-relations})} give $d^2 = 0$.
\item The resulting bar-cobar adjunction is
 Theorem~\textup{\ref{thm:bar-cobar-isomorphism-main}},
 which is the chain-level refinement of the $\infty$-categorical
 Poincar\'e--Koszul duality of Ayala--Francis~\cite{AF15}
 restricted to $n = 2$
 \textup{(}Remark~\textup{\ref{rem:ayala-francis-comparison})}.
\end{enumerate}
\end{proposition}

\begin{proof}
Part (a) is the content of \S\ref{sec:bar-cobar}: the
bar differential is $d = \sum_{i < j} \mathrm{Res}_{D_{ij}}(\eta_{ij} \wedge -)$
with $\eta_{ij}$ the FM propagator on the curve~$X$. Arnold relations
ensure $d^2 = 0$ (Corollary~\ref{cor:bar-d-squared-zero-arnold}). Part~(b):
by Remark~\ref{rem:ayala-francis-comparison}, the AF equivalence
$\int_M A \simeq \int_M A^!$ specializes at $n = 2$ to our
bar-cobar adjunction, with the factorization homology integral
computed via FM configuration space integrals.
\end{proof}

\begin{remark}[Proof status]\label{rem:en-scope}
All four parts are proved. Part~(i) by
Idrissi~\cite{Idrissi22}, who establishes that Poincar\'e duality on
configuration spaces ensures $d^2 = 0$ for the propagator-based
differential on $\mathsf{E}_n$-algebras for all~$n$. Parts~(ii)
and~(iv) by Proposition~\ref{prop:en-n2-recovery} below. Part~(iii)
follows from a chain of three results: (a)~Totaro's
presentation~\cite{Totaro96} of
$H^*(\overline{C}_k(\mathbb{R}^n))$; (b)~$\mathsf{E}_n$ formality
(Lambrechts--Voli\'c~\cite{LambrechtsVolic14}: the operadic
quasi-isomorphism $C_*(\mathsf{E}_n) \xrightarrow{\sim}
H_*(\mathsf{E}_n)$ transfers the bar-cobar adjunction to the
homological level); (c)~Knudsen's $\mathsf{E}_n$ Koszul
duality~\cite{Knudsen18}, which provides PBW and Koszul duality
theorems for higher enveloping algebras $U_n(\mathfrak{g})$.
Together, these establish that the bar cohomology of any
$\mathsf{E}_n$-algebra is governed by $\mathsf{E}_n$-operadic Koszul
duality, with the Totaro presentation providing the explicit
generators and relations.

\emph{What remains as a computational refinement} is writing down
explicit closed-form expressions for the bar differential in terms of
Totaro generators at each~$n \geq 3$; the propagator and FM
compactification exist, and $d^2 = 0$ is proved, but the individual
formulas (analogous to the Arnold-based computations at $n = 2$) have
not been tabulated. This is a concrete calculation, not a
theoretical gap.
(Contributing to Conjecture~\ref{conj:v1-master-bv-brst}.)
\end{remark}

\begin{remark}[Proof assembly for part~(iii)]\label{rem:en-proof-strategy}
\index{En-algebra@$\mathsf{E}_n$-algebra!Koszul duality!proof strategy}
Part~(iii) of Theorem~\ref{thm:en-koszul-duality} is proved by
assembling the following known ingredients into the abstract
chain-level construction.

\emph{Step~1: Formality.}
The $\mathsf{E}_n$ operad is formal over $\mathbb{Q}$ for all
$n \geq 2$: Kontsevich~\cite{Kon99} and Tamarkin~\cite{Tamarkin00}
proved this for $n = 2$;
Lambrechts--Voli\'c~\cite{LambrechtsVolic14} established the
general case via configuration space integrals on semi-algebraic
models for $\overline{C}_k(\mathbb{R}^n)$. Formality provides a
quasi-isomorphism $C_*(\mathsf{E}_n) \xrightarrow{\sim}
H_*(\mathsf{E}_n)$ of operads, so the bar-cobar adjunction can be
studied at the level of homology.

\emph{Step~2: Totaro's presentation.}
For $n \geq 3$, the cohomology ring
$H^*(\mathrm{Conf}_k(\mathbb{R}^n); \mathbb{Q})$ is generated by
degree-$(n-1)$ classes $\omega_{ij}$ ($1 \leq i < j \leq k$)
subject to: (a)~$\omega_{ij} = (-1)^n \omega_{ji}$;
(b)~$\omega_{ij}^2 = 0$; (c)~the generalized Arnold relation
$\omega_{ij}\omega_{jk} + \omega_{jk}\omega_{ki} +
\omega_{ki}\omega_{ij} = 0$~\cite{Totaro96,Coh76}. These replace
the classical Arnold relations (which govern $n = 1, 2$) with
their higher-dimensional analogues; the key difference is that the
generators sit in odd degree when $n$ is even and even degree when
$n$ is odd.

\emph{Step~3: Graph complex connection.}
Kontsevich's graph complex $\mathsf{GC}_n$ computes
$H^*(\mathrm{Aut}(\mathsf{E}_n))$, and the bar differential on
$\mathsf{E}_n$-algebras factors through $\mathsf{GC}_n$.
The passage from $n = 2$ to $n \geq 3$ is governed by the
transition from the Lie graph complex ($n = 1$) through the
associative graph complex ($n = 2$) to the commutative graph complex
($n \to \infty$); the obstruction theory at each stage is controlled
by the parity of the generators.

\emph{Step~4: Synthesis.}
The abstract construction is complete: formality (Step~1) transfers
the bar-cobar adjunction to homology; the Totaro presentation
(Step~2) provides explicit generators; Knudsen's higher enveloping
algebras~\cite{Knudsen18} identify the bar cohomology with
$\mathsf{E}_n$-operadic Koszul duality; and Idrissi's
Part~(i)~\cite{Idrissi22} ensures $d^2 = 0$ at the chain level.
What remains as a \emph{computational refinement} is writing down
the explicit bar differential formula in Totaro generators at
each~$n \geq 3$; the natural candidate propagator is the
Lambrechts--Voli\'c propagator~\cite{LambrechtsVolic14}, and the
parity of the generators (odd for even~$n$) produces sign patterns
that must be tracked through the differential.
\end{remark}

\subsection{Vassiliev invariants from Feynman transform}
\label{subsec:vassiliev}
\index{Vassiliev invariants!from Feynman transform}

\begin{conjecture}[Vassiliev invariants from bar complex;
\ClaimStatusConjectured]\label{conj:v1-vassiliev-bar}
\index{Kontsevich integral!bar complex}
For $\cA = \widehat{\fg}_k$, the Feynman transform identification
$\barB^{\mathrm{full}}(\cA) \simeq \mathrm{FT}_{\mathcal{M}\mathrm{od}}(\cA)$
\textup{(}Theorem~\textup{\ref{thm:prism-higher-genus}(ii))}
produces universal Vassiliev invariants when specialized to
configuration spaces of circles:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The restriction
 $\overline{C}_n(X) \rightsquigarrow C_n(S^1)$
 \textup{(}from complex curve to real circle\textup{)} sends the
 holomorphic propagator $\eta_{ij} = d\log(z_i - z_j)$ to the
 Kontsevich propagator $\eta_{ij}^K = \frac{1}{2\pi} d\arg(t_i - t_j)$.
\item Under this restriction, the bar complex weight systems
 $W_\Gamma\colon \fg^{\otimes n} \to \mathbb{C}$ match the
 classical weight systems of Vassiliev theory, with the
 Lie algebra $\fg$ providing the weight system as in
 Bar-Natan~\cite{BarNatan95}.
\item The genus expansion
 $\sum_g g_s^{2g-2} \barB^{(g)}$ specializes to the
 loop expansion of the Kontsevich integral.
\end{enumerate}
\end{conjecture}

\begin{proposition}[Genus-\texorpdfstring{$0$}{0} weight systems from bar complex;
\ClaimStatusProvedHere]\label{prop:vassiliev-genus0}
\index{weight system!from bar complex}
At genus~$0$, the bar complex of $\widehat{\fg}_k$ produces
classical weight systems:
\begin{enumerate}[label=\textup{(\roman*)}]
\item For each chord diagram $\Gamma$ with $n$ chords, the
 degree-$n$ bar differential $d^{(0)}\colon \barB^n \to \barB^{n-1}$
 induces a linear functional
 $W_\Gamma\colon \fg^{\otimes 2n} \to \bC$ via the residue
 pairing of the FM propagator on $\overline{C}_{2n}(\mathbb{P}^1)$.
\item These coincide with the Bar-Natan weight systems of the
 Lie algebra~$\fg$ with the Killing form at level~$k$: $W_\Gamma$
 assigns to each chord the contraction $\kappa^{ab}$ and to each
 vertex the structure constants~$f^a_{bc}$.
\end{enumerate}
\end{proposition}

\begin{proof}
At genus~$0$, the bar differential is given by residues of
the propagator $\eta_{ij} = d\log(z_i - z_j)$ along collision
divisors $D_I \subset \overline{C}_n(\mathbb{P}^1)$
(Definition~\ref{def:bar-differential-complete}). For a chord
diagram $\Gamma$ with chord $(i,j)$, the residue
$\mathrm{Res}_{z_i \to z_j} \eta_{ij}$ extracts the
OPE coefficient $J^a(z_i) J^b(z_j) \sim k \kappa^{ab}/(z_i-z_j)^2
+ f^{ab}_c J^c/(z_i-z_j)$: the double pole contributes the
Killing contraction $k\kappa^{ab}$ and the simple pole the
structure constants~$f^{ab}_c$. These are precisely the
assignments in Bar-Natan's construction of weight systems from
Lie algebras~\cite{BarNatan95}.
\end{proof}

\begin{remark}[Scope]\label{rem:vassiliev-scope}
Proposition~\ref{prop:vassiliev-genus0} establishes the genus-$0$
weight system extraction. The Feynman transform of $\mathrm{Com}$
recovers the full graph complex computing Vassiliev invariants
(Getzler--Kapranov \cite{GeK98}), and our identification
$\barB^{\mathrm{full}} \simeq \mathrm{FT}$
(Theorem~\ref{thm:prism-higher-genus}) extends this to Koszul
chiral algebras. The gap at higher genus is the passage from
complex curves to real $1$-manifolds: our propagators are
holomorphic, while Kontsevich's are real. Comparing requires an
analytic continuation argument from holomorphic to topological
Feynman transforms.
The correct bridge between holomorphic and topological frameworks is Chern--Simons gauge equivalence, not merely restriction from complex curves to $S^1$: Cattaneo--Mnev~\cite{CattaneoMnev10} establish that configuration space integrals on $3$-manifolds produce Vassiliev invariants via BV integration, and the comparison map involves the CS partition function (not a pointwise restriction of propagators).

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~VII (physics-dictionary).
The conjecture asserts that the dg Lie algebras controlling
holomorphic (chiral bar) and topological (Kontsevich integral)
deformation problems are quasi-isomorphic.
(Contributing to Conjecture~\ref{conj:v1-master-bv-brst}.)
\end{remark}

\subsection{Anomaly cancellation and Koszul structure}
\label{subsec:anomaly-koszul}
\index{anomaly!Koszul-theoretic}

\begin{theorem}[Anomaly cancellation as Koszul constraint;
\ClaimStatusProvedHere]\label{thm:anomaly-koszul}
\index{anomaly cancellation!Koszul constraint}
For the matter-ghost system
$\cA_{\mathrm{tot}} = \cA_{\mathrm{matter}} \otimes \cA_{\mathrm{ghost}}$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The obstruction coefficient is additive:
 $\kappa(\cA_{\mathrm{tot}}) = \kappa(\cA_{\mathrm{matter}}) + \kappa(\cA_{\mathrm{ghost}})$
 \textup{(}Corollary~\textup{\ref{cor:kappa-additivity})}.
\item The total bar complex is uncurved
 ($d_{\mathrm{bar}}^2 = 0$) if and only if
 $\kappa(\cA_{\mathrm{matter}}) + \kappa(\cA_{\mathrm{ghost}}) = 0$.
\item For the Virasoro matter-ghost system,
 $\kappa(\mathrm{Vir}_c) = c/2$ and
 $\kappa(\mathrm{ghost}) = c_{\mathrm{ghost}}/2 = -13$, so
 $\kappa_{\mathrm{tot}} = 0$ precisely at $c = 26$.
\end{enumerate}
\end{theorem}

\begin{proof}
Part (i) is Corollary~\ref{cor:kappa-additivity}: the singular OPE
of the tensor product is the sum of the individual singular OPEs
(the fields act on disjoint sectors), so the genus-$1$ curvature
is additive. Part~(ii) follows from
$\dfib^{\,2} = \kappa \cdot \omega_1 \cdot \mathrm{id}$
(Theorem~\ref{thm:genus-universality},
Convention~\ref{conv:higher-genus-differentials}): the total bar complex is
uncurved if and only if $\kappa_{\mathrm{tot}} = 0$. Part (iii)
is the computation $\kappa(\mathrm{Vir}_c) = c/2$
(Computation~\ref{comp:virasoro-curvature}) combined with
$c_{\mathrm{ghost}} = -26$, so
$\kappa_{\mathrm{tot}} = c/2 - 13 = 0$ at $c = 26$.
\end{proof}

\begin{theorem}[Physical anomaly cancellation, genus~\texorpdfstring{$0$}{0};
\ClaimStatusProvedHere]\label{thm:anomaly-physical-genus0}
The condition $\kappa_{\mathrm{tot}} = 0$
\textup{(}Theorem~\textup{\ref{thm:anomaly-koszul})} is equivalent,
at genus~$0$, to the BRST anomaly cancellation
$c_{\mathrm{matter}} + c_{\mathrm{ghost}} = 0$. The quasi-isomorphism
$\Phi \colon (\cA_{\mathrm{tot}}^{\mathrm{rel}}, Q_{\mathrm{BRST}})
\xrightarrow{\sim} (\barB^{\mathrm{ch}}_0(\cA_{\mathrm{tot}}),
d_{\mathrm{bar}})$ of Theorem~\textup{\ref{thm:brst-bar-genus0}}
identifies both anomaly cancellation conditions.
\end{theorem}

\begin{proof}
This is Corollary~\ref{cor:anomaly-physical-genus0}.
\end{proof}

\begin{theorem}[Physical anomaly cancellation for affine Kac--Moody algebras;
\ClaimStatusProvedHere]\label{thm:anomaly-physical-km-w}
\index{anomaly cancellation!KM/W-algebras}
For affine Kac--Moody algebras $\widehat{\fg}_k$ at
$k \neq -h^\vee$, the bar-semi-infinite comparison and anomaly
cancellation hold at genus~$0$ \emph{without restriction on the
central charge}:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Semi-infinite \textup{(}BRST\textup{)}
 cohomology is computed via the bar complex:
 $H^*(\barB(\cA)) \cong H^{\infty/2+*}(\cA)$
 \textup{(}Theorem~\textup{\ref{thm:bar-semi-infinite-km})}.
\item The anomaly duality $\kappa + \kappa' = 0$ holds for
 affine Kac--Moody algebras under Feigin--Frenkel duality
 \textup{(}Corollary~\textup{\ref{cor:anomaly-duality-km})}.
 The matter-ghost anomaly cancellation
 $\kappa_{\mathrm{tot}} = 0$ holds at
 $c = c_{\mathrm{crit}}$.
\item At genus~$0$, the algebraic Kac--Moody package relevant to
 a Chern--Simons comparison is in place:
 classical Maurer--Cartan = flatness,
 $\barB(\widehat{\fg}_k) \simeq
 C^{\infty/2+\bullet}(\widehat{\fg}_k, V_k)$, and the dual
 curvature coefficient satisfies $\kappa + \kappa' = 0$
 \textup{(}Theorem~\textup{\ref{thm:cs-koszul-km})}.
\end{enumerate}
\end{theorem}

\begin{proof}
Parts~(i) and~(ii) are restated from the cited theorems and
corollaries, which are proved using the PBW filtration,
Arkhipov functor, and Eilenberg--Moore spectral sequence
(Theorem~\ref{thm:bar-semi-infinite-km}).
Part~(iii) is the content of
Theorem~\ref{thm:cs-koszul-km}: the classical
Maurer--Cartan/flatness identification, the affine
bar--semi-infinite quasi-isomorphism, and the dual cancellation of
the curvature coefficient are all proved. The WZW/Chern--Simons
boundary interpretation remains external to the manuscript's
proved core.
\end{proof}

\begin{conjecture}[Physical anomaly cancellation, higher genus;
\ClaimStatusConjectured]\label{conj:anomaly-physical}
The genus-$0$ identifications of
Theorem~\textup{\ref{thm:anomaly-physical-km-w}} extend to all
genera: the BV-BRST identification
$\barB(\cA) \simeq C^{\mathrm{BRST}}(\cA)$ holds as a
quasi-isomorphism of \emph{genus-graded} complexes, so that the
quantum master equation
$\hbar \Delta S + \tfrac{1}{2}\{S, S\} = 0$ is the chain-level
refinement of $\Dg{g}^{\,2} = 0$ at every genus
\textup{(}Convention~\textup{\ref{conv:higher-genus-differentials})}.
\end{conjecture}

\begin{remark}[Scope]\label{rem:anomaly-scope}
The genus-$0$ case is now fully proved for two classes of
algebras:
(a)~arbitrary conformal vertex algebras at $c = 26$
(Theorem~\ref{thm:brst-bar-genus0});
(b)~Kac--Moody algebras at any non-critical level
(Theorem~\ref{thm:anomaly-physical-km-w});
(c)~for principal W-algebras obtained by DS reduction, the analogous
bar/semi-infinite transport remains conditional on
Theorem~\ref{thm:bar-semi-infinite-w}.
The remaining gap is the \emph{higher-genus} extension: at genus
$g \geq 1$, the path integral measure on
$\overline{\mathcal{M}}_g$ introduces counterterms
(Costello~\cite{costello-renormalization}) that must be matched
with the genus-$g$ bar complex. The algebraic infrastructure
is in place (curved $A_\infty$ at all genera, Feynman transform
identification); what is missing is the analytic comparison
between renormalized BRST and the bar differential at genus
$g \geq 1$. Note, however, that \emph{scalar} anomaly
cancellation extends to all genera unconditionally
for pairs with $\kappa + \kappa' = 0$:
Theorem~D (Theorem~\ref{thm:modular-characteristic})
gives $\mathrm{obs}_g(\cA) + \mathrm{obs}_g(\cA^!) = (\kappa + \kappa') \cdot \lambda_g = 0$
\textup{(}UNIFORM-WEIGHT\textup{})
for such pairs (Kac--Moody, free fields, lattice VOAs; see Theorem~D for the general formula).

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~VII (physics-dictionary).
The conjecture asserts quasi-isomorphism of the $L_\infty$ algebras
controlling BRST and bar deformation problems, genus by genus.
(Contributing to Conjecture~\ref{conj:v1-master-bv-brst}.)
\end{remark}

\subsection{\texorpdfstring{AdS$_3$/CFT$_2$ as curved Koszul duality}{AdS3/CFT2 as curved Koszul duality}}
\label{subsec:ads-cft-koszul}
\index{AdS/CFT!curved Koszul duality}

\begin{conjecture}[Holographic duality from bar-cobar;
\ClaimStatusConjectured]\label{conj:ads-cft-bar}
The curved bar complex of a boundary chiral algebra $\cA$ provides
an algebraic model for the bulk theory on AdS$_3$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The bar complex $\barB(\cA)$ classifies twisting morphisms
 (couplings between $\cA$ and $\cA^!$); the \emph{Koszul dual}
 $\cA^!$ models the line/defect sector
 \textup{(}Costello--Paquette \cite{CP2020}\textup{)}. The bulk
 \emph{observable} algebra is the derived centre
 $C^\bullet_{\mathrm{ch}}(\cA, \cA)$, not $\barB(\cA)$
 itself.
\item The curvature $m_0 = \kappa \cdot \mathbf{1}$ encodes
 the cosmological constant $\Lambda \sim -1/R_{\mathrm{AdS}}^2$,
 with $\kappa \sim c/2 \sim R_{\mathrm{AdS}}^2/\ell_P^2$.
\item The genus expansion $\sum_g g_s^{2g-2} \barB^{(g)}$
 is the $1/N$ expansion of the dual gauge theory, with
 $g_s \sim 1/N$.
\item Bar-cobar inversion $\Omega(\barB(\cA)) \simeq \cA$
 recovers the boundary algebra~(Theorem~B). The
 boundary-to-bulk map is the chiral centre construction
 $\cA \mapsto C^\bullet_{\mathrm{ch}}(\cA, \cA)$.
\end{enumerate}
\end{conjecture}

\begin{remark}[Scope]\label{rem:ads-scope}
Costello--Paquette \cite{CP2020} conjecture (footnote~8) that
curved Koszul duality controls twisted supergravity on AdS$_3$.
Our framework provides the mathematical structure they require:
the curved $A_\infty$ bar complex
(Theorem~\ref{thm:bar-ainfty-complete}), the genus expansion
(Theorem~\ref{thm:genus-universality}), and the
complementarity theorem (Theorem~\ref{thm:quantum-complementarity-main})
relating boundary and bulk. The bar--semi-infinite identification
for affine Kac--Moody algebras
\textup{(}Theorem~\ref{thm:bar-semi-infinite-km}\textup{)}
is proved, and the principal W-algebra extension remains
conditional on Theorem~\ref{thm:bar-semi-infinite-w}. Thus the
theorematic boundary algebraic package is fully in place on the
Kac--Moody side and only conditionally in place on the principal
W side. The open problem is
the bulk side of the dictionary: a filtered H-level bulk target, if
required, belongs upstream to MC4, and the comparison with twisted
supergravity is the downstream MC5 step. Concretely, the remaining gap is the
identification of the \emph{bulk} observables with the twisted
supergravity theory, which requires input from 3d gauge theory
(Chern--Simons formulation of gravity on AdS$_3$,
$\mathfrak{sl}_2 \oplus \mathfrak{sl}_2$ gauge group).

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~VII (physics-dictionary).
At H-level: an equivalence of factorization categories (boundary
chiral vs.\ bulk twisted SUGRA). The M-level model is the curved
bar complex; the S-level shadow is the $1/N$ expansion.
(Contributing to Conjecture~\ref{conj:v1-master-bv-brst}.)
\end{remark}

\begin{remark}[BRST chain map: existing ingredients]\label{rem:brst-chain-map-pieces}
\index{BRST!chain map to bar complex}
The genus-$0$ component of the bar-BRST identification already exists
in pieces in the literature:
\begin{enumerate}[label=(\roman*)]
\item Arkhipov~\cite{Arkhipov97} constructs a chain map from the
 semi-infinite (BRST) complex to the bar complex for associative
 algebras at genus~$0$.
\item Markl~\cite{Markl23} clarifies the relationship between BV
 brackets and bar complex structures via higher-order derivations.
\item Si~Li~\cite{SiLi12, SiLi16} establishes BV quantization for holomorphic
 Chern--Simons theory, producing the $A_\infty$ structure from
 Feynman diagrams; the Feynman graph integrals yield almost modular
 forms that connect to our genus expansion.
\item The Francis--Gaitsgory factorization framework~\cite{FG12}
 provides the $\infty$-categorical envelope.
\end{enumerate}
This synthesis is fully achieved for Kac--Moody algebras via
Theorem~\ref{thm:bar-semi-infinite-km}. For principal
W-algebras the corresponding genus-$0$ bar--BRST identification is
conditional on Theorem~\ref{thm:bar-semi-infinite-w}. The
higher-genus generalization is proved by
the inductive genus determination
(Theorem~\ref{thm:inductive-genus-determination})
and the HS-sewing criterion
(Theorem~\ref{thm:general-hs-sewing}).
\end{remark}

\subsection{\texorpdfstring{3d mirror symmetry from $\Eone$-chiral Koszul duality}{3d mirror symmetry from E1-chiral Koszul duality}}
\label{subsec:3d-mirror}
\index{3d mirror symmetry}

\begin{conjecture}[3d mirror symmetry;
\ClaimStatusConjectured]\label{conj:3d-mirror}
For 3d $\mathcal{N}=4$ gauge theories with Coulomb and Higgs
branches, $\Eone$-chiral Koszul duality provides the algebraic
mechanism:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The Coulomb branch algebra \textup{(}in the sense of
 Braverman--Finkelberg--Nakajima \cite{BFN18}\textup{)}
 is the $\Eone$-chiral bar complex of the Higgs branch algebra.
\item The curved $A_\infty$ structure on the bar complex
 encodes mass and FI parameter deformations.
\item Symplectic duality \textup{(}Braden--Licata--Proudfoot--Webster\textup{)}
 is the module-level avatar of $\Eone$-chiral Koszul duality
 \textup{(}Theorem~\textup{\ref{thm:e1-chiral-koszul-duality})}.
\end{enumerate}
\end{conjecture}

\begin{remark}[Scope]\label{rem:3d-mirror-scope}
This is highly speculative. The mathematical ingredients
($\Eone$-chiral Koszul duality
(Theorem~\ref{thm:e1-chiral-koszul-duality}), Yangian bar
complexes (\S\ref{sec:yangian-bar-explicit}), and the
Coulomb branch construction of \cite{BFN18}) exist
independently; the gauge-theoretic side is developed in
Bittleston--Costello--Zeng~\cite{BittlestonCostelloZeng24},
who derive 3d mirror symmetry from S-duality in the
teleparallel formulation. However, connecting them requires: (a)~identifying
the Coulomb branch ring with a specific $\Eone$-chiral bar
complex; (b)~showing that symplectic duality (exchange of Coulomb
and Higgs branches) corresponds to bar-cobar inversion; (c)~relating
the mass/FI deformations to the curvature of the bar complex.
Each of these steps requires substantial new work combining
3d gauge theory, symplectic geometry, and the $\Eone$-chiral
framework.

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~II (equivalence of homotopy categories).
The conjecture asserts an equivalence of $\Eone$-monoidal $\infty$-categories
(Coulomb branch factorization vs.\ Higgs branch bar-cobar).
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\end{remark}

\subsection{Noncommutative Hodge theory from genus tower}
\label{subsec:nc-hodge}
\index{noncommutative Hodge theory}

\begin{definition}[Chiral Hodge numbers]\label{def:chiral-hodge-numbers}
\index{Hodge numbers!chiral}
For a Koszul chiral algebra $\cA$ and genus $g \geq 1$, the
\emph{chiral Hodge numbers} are
\[
h^{p,q}_g(\cA)
\;:=\;
\dim E_2^{p,q}(\barB^{(g)}(\cA))
\]
where $E_2^{p,q}$ is the $E_2$ page of the genus spectral
sequence (Spectral Sequence~\ref{ss:genus}).
\end{definition}

\begin{proposition}[Hodge symmetry from complementarity;
\ClaimStatusProvedHere]\label{prop:nc-hodge-symmetry}
\index{Hodge symmetry!chiral}
For a Koszul chiral algebra $\cA$ with dual $\cA^!$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{(Hodge symmetry)}
 $h^{p,q}_g(\cA) = h^{q,p}_g(\cA^!)$ for all $g, p, q$.
\item \textup{(Hodge-to-de~Rham degeneration)}
 The genus spectral sequence degenerates at $E_2$
 for Koszul algebras, so that the total chiral Hodge number
 $h^n_g(\cA) = \sum_{p+q=n} h^{p,q}_g(\cA)$
 equals the hypercohomology dimension
 $\dim \mathbb{H}^n(\overline{\mathcal{M}}_g,
 \barB^{(g)}_\bullet(\cA))$.
\item \textup{(Self-dual Hodge diamond)}
 If $\cA \simeq \cA^!$ \textup{(}self-dual\textup{)},
 then $h^{p,q}_g(\cA) = h^{q,p}_g(\cA)$.
\end{enumerate}
\end{proposition}

\begin{proof}
Part (i): Theorem~\ref{thm:quantum-complementarity-main}
provides the complementarity isomorphism
$E_2^{p,q}(\cA) \cong E_2^{q,p}(\cA^!)^\vee$, which gives
$h^{p,q}_g(\cA) = h^{q,p}_g(\cA^!)$. Part (ii): the $E_2$
collapse for Koszul algebras is
Theorem~\ref{thm:bar-cobar-spectral-sequence}. Part (iii)
is immediate from (i).
\end{proof}

\begin{remark}[Hodge symmetry from universal MC duality]
\label{rem:hodge-theta}
The Hodge symmetry $h^{p,q}_g(\cA) = h^{q,p}_g(\cA^!)$
has a transparent origin in the universal Maurer--Cartan
class (Theorem~\ref{thm:explicit-theta}): Verdier duality
sends $\Theta_\cA \mapsto -\Theta_{\cA^!}$, which
exchanges the $E_2$ pages of $\cA$ and $\cA^!$
(underlying complexes:
$\mathbb{D}(\barB^{(g)}(\cA)) \simeq (\cA^!)^{(g)}_\infty$, factorization \emph{algebra}, not coalgebra).
For self-dual algebras ($\cA \simeq \cA^!$), this gives an internal
involution on the deformation package and hence a symmetric chiral
Hodge diamond. Self-duality alone does \emph{not} force
$\Theta_\cA$ or $\kappa(\cA)$ to vanish; it only constrains how the
Hodge pages are paired. The strongest uncurved form occurs on the
scalar-critical locus $\kappa = 0$, where
$\Theta_\cA^{\min} = 0$ and the bar complex is uncurved.
\end{remark}

\begin{remark}[Computability of the weight filtration]\label{rem:weight-filtration-computable}
The weight filtration on $H^*(\overline{C}_n(X))$ that enters the genus spectral sequence $E_2^{p,q}$ is explicitly computable by combinatorial methods. Bibby--Gadish~\cite{BG24} establish effective algorithms for computing the mixed Hodge structure on configuration space cohomology via intersection lattice data. For our chiral Hodge numbers $h^{p,q}_g(\cA)$, this means the $E_2$ page can in principle be computed from the combinatorial data of the Orlik--Solomon algebra (for genus~$0$) and the augmented OS algebra (for genus~$g \geq 1$), without needing the full geometric machinery of mixed Hodge modules.
\end{remark}

\begin{conjecture}[Twistor interpretation of genus expansion;
\ClaimStatusConjectured]\label{conj:nc-hodge}
The genus expansion variable $g_s$ in the total bar complex
$\barB^{\mathrm{total}}(\cA) = \sum_g g_s^{2g-2}\, \barB^{(g)}(\cA)$
plays the role of the twistor parameter $\lambda$ in the
Kontsevich--Soibelman noncommutative Hodge
theory~\cite{KontsevichSoibelman}: there exists a
$\mathbb{C}^*$-action on the de~Rham complex of the genus tower
such that the weight-$k$ subspace at genus~$g$ has dimension
$h^{k,n-k}_g(\cA)$.
\end{conjecture}

\begin{remark}[Scope]\label{rem:nc-hodge-scope}
The Hodge numbers and their symmetry are proved
(Proposition~\ref{prop:nc-hodge-symmetry}), and the $E_2$
degeneration is established
(Theorem~\ref{thm:bar-cobar-spectral-sequence}). The remaining
conjecture is the identification with the Kontsevich--Soibelman
$\mathbb{C}^*$-action, which requires establishing a twistor
structure on the genus tower. There is currently no framework
in which to formulate this precisely for chiral algebras.

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~III
(shifted-symplectic/Lagrangian enhancement). The conjecture
upgrades the genus spectral sequence to a $\mathbb{C}^*$-equivariant
shifted-symplectic structure on the total deformation complex.
(Part of the MC2 theorem package; the universal class exists by
Theorem~\ref{thm:mc2-bar-intrinsic}, while the older comparison
route is Theorem~\ref{thm:mc2-full-resolution}.)
\end{remark}

\subsection{Analytic completion and the sewing envelope}
\label{subsec:analytic-completion-programme-editorial}
\index{analytic completion!research programme}

\begin{conjecture}[Analytic completion programme;
\ClaimStatusConjectured]\label{conj:analytic-completion-programme}%
The algebraic bar-cobar engine admits a canonical analytic completion:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Sewing envelope}: the Hausdorff completion
 $\cA^{\mathrm{sew}}$ for the locally convex topology generated by
 sewing-amplitude seminorms is a universal analytic completion of
 the algebraic chiral core
 (Definition~\ref{def:sewing-envelope}).
\item \emph{HS-sewing criterion}: under Hilbert--Schmidt sewing
 (Definition~\ref{def:hs-sewing}), closed amplitudes become trace
 class and partition functions converge
 (Proposition~\ref{prop:hs-trace-class}).
\item \emph{Analytic Koszul duality}: the genus-zero bar-cobar
 adjunction lifts to an equivalence of complete analytic module
 categories (Definition~\ref{def:analytic-koszul-pair}).
\item \emph{Coderived shadows}: at curved genus, the analytic shadow
 $Q_g^{\mathrm{an}}(\cA)$ lives in the coderived analytic category
 (Definition~\ref{def:analytic-shadow}); the shadow partition
 function~\eqref{eq:shadow-partition-function} is a convergent
 supertrace.
\end{enumerate}
The decisive test case is the Heisenberg VOA, where the sewing
envelope should be $\operatorname{Sym} A^2(D)$
\textup{(}Theorem~\textup{\ref{thm:heisenberg-sewing}}\textup{)}.
Recent work: Moriwaki~\cite{Moriwaki26a, Moriwaki26b} constructs
conformally flat factorization homology valued in
$\operatorname{IndHilb}$; Adamo--Moriwaki--Tanimoto~\cite{AMT24} prove
conformal Osterwalder--Schrader axioms for unitary full VOAs.
\end{conjecture}

\begin{remark}[Scope]\label{rem:analytic-programme-scope}
All items are \ClaimStatusConjectured{}. The Moriwaki construction
is explicitly $1$-categorical, metric-dependent, and restricted to
conformally flat geometry; the explicit VOA-level example is the
Heisenberg; extension to general unitary full VOAs is an expectation
rather than a completed theorem. The programme is orthogonal to the
algebraic proved core (Theorems~A--H); it asks whether the formal
shadow invariants of \S\ref{sec:analytic-completion} survive analytic
completion and become positivity-compatible invariants.

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~V
(filtered/pro-object comparison). The algebraic bar complex is the
dense pro-algebraic skeleton; the analytic completion is the intended
H-level target.
(Part of the MC5 frontier; genus~$\geq 2$ requires analytic
control.)
\end{remark}

\subsection{The nine directions: overview and interdependence}
\label{subsec:programme-synthesis}
\index{research directions!interdependence}

Programmes~I (higher-dimensional Koszul duality,
\S\ref{subsec:higher-dim-kd}) and~II (Vassiliev invariants,
\S\ref{subsec:vassiliev}) share the critical-level bar complex
as common foundation, but diverge in application: Programme~I
computes $\mathsf{E}_n$-operadic Koszul duals via configuration
space integrals on $n$-manifolds, while Programme~II specializes
from complex curves to real circles, extracting knot invariants via
the Kontsevich integral. At $n = 3$, the two programmes converge:
the $\mathsf{E}_3$-bar complex on a $3$-manifold computes
perturbative Chern--Simons invariants, and the restriction to
configuration spaces of circles in $S^3$ produces precisely the
Vassiliev weight systems of Programme~II
(Proposition~\ref{prop:vassiliev-genus0}).

The anomaly cancellation programme
(\S\ref{subsec:anomaly-koszul}) is the physical interpretation of
the curvature theory: $\kappa_{\mathrm{tot}} = 0$ is both the
mathematical condition $d_{\mathrm{bar}}^2 = 0$ and the
physical condition for consistent quantization
(Theorem~\ref{thm:anomaly-koszul}). This feeds directly into the
AdS$_3$/CFT$_2$ programme (\S\ref{subsec:ads-cft-koszul}), where
the curvature $m_0 = \kappa \cdot \mathbf{1}$ plays the role of
the cosmological constant: the bar-cobar adjunction
$\barB(\cA) \dashv \Omega(\barB(\cA))$ models the
boundary-to-bulk and bulk-to-boundary maps of holographic duality.
The $3$d mirror symmetry programme (\S\ref{subsec:3d-mirror})
extends this physical circle from $2$d to $3$d, with
$\Eone$-chiral Koszul duality
(Theorem~\ref{thm:e1-chiral-koszul-duality}) replacing the
$\Etwo$-chiral theory and Coulomb--Higgs exchange replacing
bar-cobar inversion.

The noncommutative Hodge programme (\S\ref{subsec:nc-hodge})
reinterprets the entire genus tower as a twistor family: the
genus expansion variable $g_s$ plays the role of the
Kontsevich--Soibelman twistor parameter, and the chiral Hodge
numbers $h^{p,q}_g(\cA)$ provide the Hodge-theoretic data.
This programme depends on the complementarity theorem
(Theorem~\ref{thm:quantum-complementarity-main}), which supplies
the Hodge symmetry $h^{p,q}_g(\cA) = h^{q,p}_g(\cA^!)$.

\begin{remark}[Unifying vision: modular Koszul duality for
factorization algebras]\label{rem:unifying-vision}
\index{modular Koszul duality!unifying conjecture}
All of the programmes above are facets of a single conjecture:
for a factorization algebra~$\mathcal{F}$ on an oriented
$n$-manifold~$M$, the Feynman transform
$\mathrm{FT}(\mathcal{F})$ computes the Koszul dual
factorization algebra on~$M$ with reversed orientation.
The evidence is the following hierarchy of established and
conjectural instances:
\begin{enumerate}[label=\textup{(\roman*)}]
\item At $n = 1$ \textup{(}$A_\infty$-algebras\textup{)}:
 classical bar-cobar duality
 \textup{(}Loday--Vallette~\cite{LV12}\textup{)}. This is the
 foundational case, with the bar and cobar constructions as mutual
 inverses on the Koszul locus.
\item At $n = 2$ with complex structure
 \textup{(}chiral algebras\textup{)}: the Main Theorems~A, B, C
 of this monograph
 \textup{(}Theorems~\ref{thm:bar-cobar-isomorphism-main},
 \ref{thm:higher-genus-inversion},
 \ref{thm:quantum-complementarity-main}\textup{)}. The Feynman
 transform is realized by Verdier duality on FM compactifications,
 and the genus expansion provides the quantum corrections.
\item At $n = 2$ topological
 \textup{(}$\mathsf{E}_2$-algebras\textup{)}: Kontsevich
 formality~\cite{Kon03}, which identifies the $\mathsf{E}_2$-bar
 complex with the deformation complex of the associative operad.
\item At $n = 3$
 \textup{(}$\mathsf{E}_3$-algebras\textup{)}:
 perturbative Chern--Simons invariants, with Vassiliev weight
 systems extracted from the $\mathsf{E}_3$-bar complex
 \textup{(}Conjecture~\ref{conj:v1-vassiliev-bar}\textup{)}.
\item At $n = \infty$
 \textup{(}$\mathsf{E}_\infty$-algebras\textup{)}:
 factorization homology duality of
 Ayala--Francis~\cite{AF15}, which provides the
 $\infty$-categorical framework for Poincar\'e--Koszul
 duality on arbitrary manifolds.
\end{enumerate}
This monograph provides case~(ii) in full detail; the passage
from (ii) to the general conjecture is the content of
\S\ref{sec:modular-koszul-programme}. For the status of
each programme-level aspiration, see
\S\ref{subsec:nine-futures}.
\end{remark}



\section{Programme status assessment}
\label{sec:programme-status-assessment}

\subsection{Status: nine futures}\label{subsec:nine-futures}
\index{modular Koszul duality!status}

The development of this monograph was guided by nine programme-level
aspirations. We summarize the status of each, then record the
working definition and the concrete modular datum that constitute
the realized core.

\medskip

\noindent\textbf{Future~1} (all-genus parameterized bar-cobar theory):
\textbf{proved} after reformulation. The correct parameter source
is fiber cohomology $H^1(\Sigma_g, \mathbb{C})$, not moduli cohomology
$H^1(\mathcal{M}_g)$ (which vanishes for $g \geq 2$ by Harer).
The total corrected differential $\Dg{g}$ satisfies
$\Dg{g}^{\,2} = 0$ (Theorem~\ref{thm:quantum-diff-squares-zero}),
with fiberwise curvature $\dfib^{\,2} = \kappa(\cA)\cdot\omega_g$
(Theorem~\ref{thm:quantum-arnold-relations}).

\noindent\textbf{Future~2} (modular Koszul programme):
\textbf{largely realized.}
Theorems~A--D and~H establish the core; MC2 is fully resolved
(Theorem~\ref{thm:universal-MC}). The remaining gap is the
coderived Ran-space formalism (\S\ref{subsec:coderived-ran}).

\noindent\textbf{Future~3} (modular homotopy theory for factorization
algebras on curves): the mature endpoint of the project.
The working definition appears below
(Definition~\ref{def:modular-homotopy-theory-working}).

\begin{definition}[Modular homotopy theory: working definition]
\label{def:modular-homotopy-theory-working}
\index{modular homotopy theory!working definition}
A \emph{modular homotopy theory} on a smooth curve~$X$ is the
global completion of the nilpotence-periodicity correspondence
(Remark~\ref{rem:nilpotence-periodicity}) from genus~$0$ to all
genera. Concretely, it consists of:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{The categorical $\exp/\log$ adjunction.} An
 $\infty$-categorical bar-cobar adjunction
 $\barB_X \dashv \Omega_X$ on the coderived category
 $D^{\mathrm{co}}(\operatorname{Fact}(X))$ of curved factorization
 algebras on $\operatorname{Ran}(X)$: the categorical logarithm and
 its inverse, analytically continued to the multi-valued regime via
 the coderived framework.
\item \emph{Functoriality of the logarithm over moduli.}
 Functoriality of the adjunction over the modular operad
 $\{\overline{\mathcal{M}}_{g,n}\}_{g,n}$, intertwined with Verdier
 duality:
 $\mathbb{D}_{\operatorname{Ran}}\,\barB_X(\cA)
 \simeq \cA^!_\infty$ (factorization \emph{algebra},
 not coalgebra). The monodromy of the logarithm varies
 coherently over moduli.
\item \emph{The complete logarithm.} A universal Maurer--Cartan class
 $\Theta_{\cA} \in
 \operatorname{MC}(\operatorname{Def}_{\mathrm{cyc}}(\cA)
 \,\widehat{\otimes}\,
 R\Gamma(\overline{\mathcal{M}}_{g,\bullet}, \mathbb{Q}))$
 controlling the genus tower as a single deformation: the full
 logarithmic datum from which the characteristic hierarchy
 (Remark~\ref{rem:characteristic-hierarchy}) and
 its exponential (the modular automorphy) are derived.
\item \emph{The Lagrangian branch structure.} A shifted-symplectic
 pairing on
 $R\Gamma(\overline{\mathcal{M}}_g, \mathcal{Z}_{\cA})$
 for which the deformation and obstruction complexes
 $Q_g(\cA)$, $Q_g(\cA^!)$ are complementary Lagrangians: the
 branch structure of the categorical logarithm, with each
 branch (algebra vs.\ Koszul dual) contributing a Lagrangian
 half of the total monodromy.
\end{enumerate}
\end{definition}

\noindent
Of these four requirements: (ii) and (iv) are proved
(Theorems~A, C; Proposition~\ref{prop:ptvv-lagrangian}),
where (ii) is established as functorial compatibility over
$\overline{\mathcal{M}}_{g,n}$ rather than as an equivalence of
modular operads;
(i) is proved at genus~$0$ and on the Koszul locus at all genera
(Theorems~A, B); (iii) is resolved by
Theorem~\ref{thm:mc2-bar-intrinsic}
(see also Theorem~\ref{thm:universal-MC}); the older
comparison route of Theorem~\ref{thm:mc2-full-resolution} is now
understood as a scalar-lane refinement.

\begin{theorem}[Volume~I concrete modular datum;
\ClaimStatusProvedHere]
\label{thm:volume-one-concrete-modular-datum}
Let $\cA$ be a modular Koszul chiral algebra on a smooth projective
curve~$X$. The present theorem surface supplies a concrete modular
datum, separated by semantic level:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{H-level.}
 Definition~\ref{def:modular-koszul-homotopy} provides the
 homotopy bar object $\mathbf{B}_X(\cA)$, the dual object~$\cA^!$,
 and the center local system~$\mathcal{Z}_{\cA}$, with Verdier
 intertwining and Lagrangian complementarity supplied by
 Theorems~\ref{thm:bar-cobar-isomorphism-main}
 and~\ref{thm:quantum-complementarity-main}. The cyclic deformation
 object $\Defcyc(\cA)$ and the universal Maurer--Cartan
 class~$\Theta_{\cA}$ exist by the bar-intrinsic construction
 (Theorem~\ref{thm:mc2-bar-intrinsic}), without restriction to
 simple Lie symmetry.
\item \emph{M-level.}
 Definition~\ref{def:modular-koszul-chiral} provides the dg bar
 model~$\barB_X(\cA)$ together with the genus-$0$ differential
 $\dzero$, the fiberwise curved differential~$\dfib$, and the total
 corrected differential~$\Dg{g}$, satisfying
 $\dzero^{\,2} = 0$,
 $\dfib^{\,2} = \kappa(\cA)\,\omega_g$,
 and $\Dg{g}^{\,2} = 0$
 by Theorems~\ref{thm:bar-nilpotency-complete},
 \ref{thm:genus-universality},
 and~\ref{thm:quantum-diff-squares-zero}.
\item \emph{S-level.}
 Definition~\ref{def:full-modular-package} packages the scalar,
 spectral, periodic, and genus-family shadows as
 $\mathcal{C}_{\cA}
 = (\Theta_{\cA}, \kappa(\cA), \Delta_{\cA}, \Pi_{\cA},
 \mathcal{H}_{\cA})$.
 Here $\kappa(\cA)$ is proved by
 Theorem~\ref{thm:modular-characteristic},
 $\Delta_{\cA}$ by
 Theorem~\ref{thm:discriminant-spectral},
 $\Pi_{\cA}$ has a proved structural framework by
 Remark~\ref{rem:periodicity-triple},
 and $\mathcal{H}_{\cA}$ is the genus-graded deformation family
 induced by~$\Theta_{\cA}$ when the latter is available.
\end{enumerate}
\end{theorem}

\begin{proof}
The H-level datum is exactly
Definition~\ref{def:modular-koszul-homotopy}, together with
Theorems~\ref{thm:bar-cobar-isomorphism-main}
and~\ref{thm:quantum-complementarity-main}; the universal
Maurer--Cartan enhancement is supplied intrinsically by
Theorem~\ref{thm:mc2-bar-intrinsic}, while
Theorem~\ref{thm:mc2-full-resolution} is the scalar-lane comparison
refinement on the simple-Lie-symmetry locus. The M-level dg model is
Definition~\ref{def:modular-koszul-chiral}, and its three
differential identities are the cited theorems on genus-$0$
nilpotency, genus-$g$ curvature, and corrected nilpotence. The
S-level hierarchy is
Definition~\ref{def:full-modular-package}, with the scalar,
spectral, and periodic statements supplied by the cited theorem and
remark references.
\end{proof}

\begin{remark}[What remains open]
\label{rem:volume-one-concrete-modular-datum-frontier}
The remaining open problems concern the outer continuation of this datum: coderived
bar-cobar persistence beyond the proved loci, the H-level MC4 coefficient identities for
$\mathcal{W}_\infty$ and Yangian towers, non-principal W-algebra duality, and analytic completion.
\end{remark}

\noindent\textbf{Future~4} (universal modular characteristic hierarchy):
\textbf{existence proved.}
The full characteristic quintuple
$\mathcal{C}_{\cA} = (\Theta_{\cA}, \kappa(\cA), \Delta_{\cA},
\Pi_{\cA}, \mathcal{H}_{\cA})$
(Definition~\ref{def:full-modular-package}) exists unconditionally:

\begin{itemize}[nosep]
\item $\kappa(\cA)$: proved (Theorem~\ref{thm:modular-characteristic});
\item $\Delta_{\cA}(x) = \det(1 - x\,T_{\mathrm{rec}})$: proved
 (Theorem~\ref{thm:discriminant-spectral};
 Definition~\ref{def:spectral-branch-object});
\item $\Pi_{\cA}$: structural framework proved
 (Remark~\ref{rem:periodicity-triple};
 Definition~\ref{def:derived-scalar-period}), though
 specific sharp modular and geometric periods remain conjectural
 (Future~7). Under the nilpotence-periodicity correspondence
 (Remark~\ref{rem:nilpotence-periodicity}), $\Pi_{\cA}$ is the
 \emph{exponential} of the logarithmic data
 $(\kappa(\cA), \Delta_{\cA}, \Theta_{\cA})$: the periodicity
 profile is derived from the nilpotent characteristic via
 exponentiation, not an independent invariant;
\item $\Theta_{\cA}$: \textbf{proved}
 (Theorem~\ref{thm:mc2-bar-intrinsic}), resolving
 Theorem~\ref{thm:universal-MC} intrinsically from the
 genus-completed bar differential. The older explicit
 completion route
 (Theorem~\ref{thm:mc2-full-resolution}) now gives the
 all-genera scalar-trace package only on the proved
 uniform-weight lane, with genus~$1$ universal separately;
\item $\mathcal{H}_{\cA}$: the genus-graded deformation family
 exists as a formal consequence of $\Theta_{\cA}$.
\end{itemize}

Scalar saturation is proved on the standard landscape
(Corollary~\ref{cor:effective-quadruple}); sharp modular periods
and functoriality under embeddings remain open.

\noindent\textbf{Future~5} (index-theoretic genus expansions):
\textbf{realized}
(Theorem~\ref{thm:family-index}).

\noindent\textbf{Future~6} (derived Drinfeld--Kohno and quantum
groups): \textbf{substantially realized}, decomposed into a DK
ladder. DK-0 through DK-$1\frac{1}{2}$ are proved. DK-2/3 is
proved for the evaluation-generated core at all simple types
(Corollary~\ref{cor:dk23-all-types}); for fd type~$A$,
Conjecture~\ref{conj:dk-fd-typeA} supplies only the conditional
thick-generation extension criterion once the ambient
extension/comparison package is constructed; Koszulness uses Molev
PBW~\cite{molev-yangians}).
DK-4 is reduced to the algebraic identification of the tangent
Lie algebra with the dg-shifted Yangian
(Conjecture~\ref{conj:dk4-inverse-limit}), after the
Mittag-Leffler property for the RTT tower
(Theorem~\ref{thm:rtt-mittag-leffler}) and the completed bar-cobar
equivalence for Yangians
(Corollary~\ref{cor:completed-bar-cobar-yangian}).
DK-5 remains conjectural
(Conjecture~\ref{conj:full-dk-bridge}).

\begin{remark}[The category~\texorpdfstring{$\mathcal{O}$}{O}
generation obstruction]
\label{rem:cat-o-generation-obstruction}
\index{Category O@Category $\mathcal{O}$!generation problem}
\index{thick generation!Category O@Category $\mathcal{O}$}
The generated-core DK comparison surface
\textup{(}traditionally packaged as DK-2/3\textup{)} is resolved on the
evaluation-generated core at all simple
types (Corollary~\ref{cor:dk23-all-types}). Beyond this core, the
natural domain for thick generation is
$\mathcal{O}_{\mathrm{poly}}$ (polynomial subcategory); thick
generation holds there for $N = 2$ unconditionally and for all~$N$
(Theorem~\ref{thm:catO-thick-generation}). By
Lemma~\ref{lem:fd-thick-closure}, the thick closure of
evaluation modules in $D^b(\mathcal{O})$ equals
$D^b(\mathcal{O}_{\mathrm{poly}})$ and cannot reach
infinite-length modules. For infinite-dimensional modules, the
correct framework is localizing generation in a completed/coderived
category; what is proved here is the evaluation-generated-core DK
surface, while the remaining completion packet beyond that core stays
open.
Candidate strategies are developed in
\S\ref{sec:cat-O-strategies}.
\end{remark}

\noindent\textbf{Future~7} (periodicity and tautological depth):
\textbf{conceptually corrected.}
The geometric contribution is nilpotent (not periodic):
$\kappa(\lambda)^{g-1} = 0$ on smooth moduli
(Theorem~\ref{thm:geometric-depth-smooth}). Quantum periodicity
is proved unconditionally; modular bar periodicity remains
conjectural
(Conjectures~\ref{conj:modular-periodicity-minimal}
and~\ref{conj:modular-periodicity-wzw}).

\noindent\textbf{Future~8} (spectral discriminant geometry):
\textbf{proved.}
$\Delta_{\cA}(x) = \det(1 - x\, T_{\mathrm{rec}})$ is established
(Theorem~\ref{thm:discriminant-spectral}) with DS invariance
(Theorem~\ref{thm:ds-bar-gf-discriminant}).

\noindent\textbf{Future~9} (BV/BRST/path-integral completion):
genus-$0$ proved (Theorem~\ref{thm:brst-bar-genus0});
higher genus proved via inductive genus determination
(Theorem~\ref{thm:inductive-genus-determination}),
two-dimensional convergence
(Proposition~\ref{prop:2d-convergence}),
and the HS-sewing criterion
(Theorem~\ref{thm:general-hs-sewing}); see also
(Remark~\ref{rem:bv-equals-bar-cobar},
Conjecture~\ref{conj:v1-bar-cobar-path-integral}).
Volume~II's bar--cobar Quillen equivalence (now unconditional)
supplies the operadic identification needed for the disk-local
packet; the remaining content is the analytic genus-lifting.

\begin{remark}[Summary of the nine futures]\label{rem:nine-futures-summary}
\index{modular Koszul duality!nine futures}
Of the nine programme-level aspirations:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{@{}clp{5.5cm}@{}}
\toprule
\textbf{\#} & \textbf{Future} & \textbf{Status} \\
\midrule
1 & $H^1(\mathcal{M}_g)$-parameterized theory & \textbf{Proved} \\
2 & Modular Koszul programme & \textbf{Largely realized} \\
3 & Modular homotopy theory & Alive (Def.~\ref{def:modular-homotopy-theory-working}) \\
4 & Universal char.\ package & \textbf{Core proved with one repaired gap}: standard landscape (Cor.~\ref{cor:effective-quadruple}) gives the effective \(\Gamma\)-quadruple, generic cyclic rigidity (Thm~\ref{thm:cyclic-rigidity-generic}) and algebraic-family rigidity at all non-critical levels (Thm~\ref{thm:algebraic-family-rigidity}) give vanishing primitive tangent space and level-direction concentration, and the repaired equivalence (Prop.~\ref{prop:saturation-equivalence}) matches that weaker statement; the strong scalar identity $\Theta_{\cA}^{\min}=\kappa(\cA)\eta\otimes\Lambda$ is proved on the uniform-weight lane and \emph{fails} for multi-weight families: the genus-$g$ free energy receives a cross-channel correction (Theorem~\ref{thm:multi-weight-genus-expansion}, resolving Open Problem~\ref{op:multi-generator-universality} negatively); functoriality (Prop.~\ref{prop:saturation-functorial}) is one-channel generically and scalar only on the proved lane; $\Pi_{\cA}$ sharp open \\
5 & Index genus expansions & \textbf{Realized} (Thm~\ref{thm:family-index}) \\
6 & Derived Drinfeld--Kohno & DK-0/1/$1\frac{1}{2}$ proved; generated-core DK comparison surface \textup{(}traditionally packaged as DK-2/3\textup{)} proved on the evaluation-generated core for all types \textup{(}uses Molev PBW\textup{)}; $\mathcal{O}_{\mathrm{poly}}$ belongs to the separate type-$A$ thick-generation lane; full $\mathcal{O}$/KL extension conjectural; Positselski/ind-completion/ML theorem; DK-4/5 formalized \\
7 & Periodicity \& tautological depth & Corrected: geometric contribution is nilpotent depth (proved, index $\leq g-1$); quantum proved; modular bar periodicity conjectural \\
8 & Spectral discriminant & \textbf{Proved} + branch (Def.~\ref{def:spectral-branch-object}) \\
9 & BV/BRST completion & Genus~$0$ proved; genus~$1$ bridge proved (Feynman curvature = $\kappa \cdot \omega_1$); Quillen equiv.\ unconditional; $g \geq 2$ analytic \\
\bottomrule
\end{tabular}
\end{center}
\noindent
The project is becoming \emph{modular homotopy theory for
factorization algebras on curves}: the global completion of the
nilpotence-periodicity correspondence
(Remark~\ref{rem:nilpotence-periodicity}) from genus~$0$ to all
genera. Its structural identity is the principle that
\emph{nilpotence is the logarithm of periodicity}: the bar
construction is the categorical logarithm whose single-valued
regime recovers, via formal-disk restriction, classical Koszul duality over a point (the degree-$2$ stratum) and whose
multi-valued regime is the full chiral theory (already at genus~$0$, configuration-space topology on curves has more structure than the classical picture over a point; at genus~$g \geq 1$, Hodge curvature enters); the
curvature $\kappa(\cA)$ is the infinitesimal generator of the
monodromy; the coderived category is the analytic continuation; the
characteristic hierarchy
(Remark~\ref{rem:characteristic-hierarchy}) organizes the
logarithmic data ($\kappa$, $\Delta$, $\Theta$) from which the
periodic data ($N$, $\Pi$, modular automorphy) are derived via
exponentiation.

The monograph realizes this identity through a GRR genus theorem
(Future~5), a spectral characteristic package (Futures~4, 8), and a
staged derived Drinfeld--Kohno ladder beyond the evaluation locus
(Future~6). It is no longer becoming a single theorematic theory
of all-genus corrections controlled by $H^1(\mathcal{M}_g)$
parameters (Future~1, superseded) or a sharp global periodicity
theorem (Future~7, stratified). These older self-images have been
replaced by the nilpotence-periodicity framework, which correctly
classifies the geometric contribution as nilpotent depth (not
period), derives modular periodicity from the scalar
characteristic via exponentiation, and identifies the Koszul locus
as the convergence domain of the categorical logarithm.
\end{remark}

\begin{remark}[Status notes from the conjecture census]
\label{rem:constitution-status-updates}
\index{conjecture census!status updates}
\index{programme status!conjecture census updates}
The current conjecture census forces the following programme-level
status notes:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The modular factorization adjunction
 $U^{\mathrm{mod}}_X \dashv \operatorname{Prim}^{\mathrm{mod}}$
 is \textbf{proved}
 (Theorem~\ref{thm:platonic-adjunction}).
\item The all-types categorical Clebsch--Gordan packet of MC3 is now
 \textbf{proved}
 (Theorem~\ref{thm:categorical-cg-all-types}),
 while the remaining completion packets stay open beyond the
 evaluation-generated core. The folding approach
 (Proposition~\ref{rem:mc3-type-b-folding}) provides an alternative
 route for types $B_n$ and $C_n$.
\item Transport-closure of hook vertices equals
 $\operatorname{Par}(N)$ for all $N \leq 7$
 (Theorem~\ref{thm:transport-closure-type-a}).
\item The formality route (derived DS $=$ classical DS by
 Kazhdan formality (more precisely, $E_1$ degeneration of the
 Kazhdan filtration spectral sequence)) resolves DS--Koszul
 intertwining for all abelian-$\mathfrak{n}_+$ orbits
 (Proposition~\ref{prop:ds-bar-formality}).
\end{enumerate}
\end{remark}


\subsection{Index of conjectures and related results}\label{sec:conjecture-index}
\index{conjectures!index}

The following conjectures and related results are organized by theme.
Each entry gives the label, a brief description,
and the section where it appears.

\smallskip
\noindent\textbf{Algebraic structure.}

\begin{itemize}[nosep]
\item Conjecture~\ref{conj:anomaly-cancellation}:
 Anomaly cancellation implies uncurved duality
 (\S\ref{sec:first-complete-proof}).
\item Conjecture~\ref{conj:brst-cohomology}:
 Heuristic BRST/bar comparison, general genus
 (\S\ref{sec:first-complete-proof}).
\item Conjecture~\ref{conj:cobar-physical}:
 Cobar elements as on-shell propagator templates
 (\S\ref{sec:first-complete-proof}).
\item Conjectures~\ref{conj:modular-periodicity-minimal},
 \ref{conj:modular-periodicity-wzw},
 \ref{conj:modular-periodicity}:
 Modular periodicity of bar cohomology (conjectured for
 minimal models, WZW, and general rational chiral algebras;
 $T$-matrix periodicity proved unconditionally)
 (\S\ref{sec:km-koszul-abstract}).
\item Conjecture~\ref{conj:reflected-modular-periodicity}:
 Reflected periodicity for non-self-dual algebras
 (\S\ref{sec:km-koszul-abstract}).
\item Conjecture~\ref{conj:w-infty-bar}:
 downstream large-$N$ inverse-limit specialization of the standard
 $\mathcal{W}_\infty$ MC4 package
 (\S\ref{sec:w3-bar-degree3}).
\end{itemize}

\smallskip
\noindent\textbf{Representation theory and Langlands.}

\begin{itemize}[nosep]
\item Conjectures~\ref{conj:kl-periodic-cdg}--\ref{conj:kl-braided}:
 Kazhdan--Lusztig recovery from bar-cobar (three stages:
 periodic CDG, coderived lift, braided semisimplified target;
 \S\ref{subsec:kl-from-bar-cobar}).
\item Conjecture~\ref{conj:full-derived-dk}:
 Factorization-categorical DK/KL bridge beyond the evaluation locus
 (\S\ref{sec:derived-dk}).
\item Conjecture~\ref{conj:coha-koszul}:
 CoHA Koszulness for quiver varieties
 (\S\ref{sec:yangian-bar-explicit}).
\item Conjecture~\ref{conj:shifted-yangian-langlands}:
 Shifted Yangian and geometric Langlands
 (\S\ref{sec:yangian-bar-explicit}).
\item Conjecture~\ref{conj:e1-genus-theory}:
 $\Eone$-chiral genus theory for Yangians
 (\S\ref{sec:yangian-bar-explicit}).
\item Conjecture~\ref{conj:mc3-sectorwise-all-types}:
 sectorwise DK extension to the completed/coderived MC3 domain for
 all types
 (\S\ref{sec:cat-O-strategies}). $E_1$ sub-exponential growth is
 proved
 (Proposition~\ref{prop:lqt-e1-subexponential-growth}), and
 sectorwise convergence on the evaluation-generated core is proved
 (Theorem~\ref{thm:sectorwise-spectral-convergence}); the open step
 is extension of this package to the completed/coderived
 enlargement.
\item Conjecture~\ref{conj:factorization-finiteness-criterion}:
 Factorization finiteness criterion (abstract bypass of thick
 generation; \S\ref{sec:categorical-logarithm}).
\end{itemize}

\smallskip
\noindent\textbf{Generating functions and combinatorics.}
\begin{itemize}[nosep]
\item Conjecture~\ref{conj:sl3-bar-gf}:
 $\widehat{\mathfrak{sl}}_3$ bar generating function
 (\S\ref{sec:sl3-computation}).
% conj:sl3-discriminant merged into conj:sl3-bar-gf (single conjecture block)
\item Conjecture~\ref{conj:non-simply-laced-discriminant}:
 Non-simply-laced discriminant families
 (\S\ref{subsec:bernoulli-asymptotics}).
\item Conjecture~\ref{conj:w3-algebraicity}:
 $\mathcal{W}_3$ bar algebraicity
 (\S\ref{sec:w3-bar-degree3}).
 Seven independent consistency checks support $H^5 = 171$
 (Appendix~\ref{subsec:w3-h5-verification}).
\item Conjecture~\ref{conj:yangian-bar-gf}:
 Yangian bar generating function
 (\S\ref{sec:yangian-bar-explicit}).
 Seven independent consistency checks support $H^4 = 82$
 (Appendix~\ref{subsec:yangian-h4-verification}).
\item Conjecture~\ref{conj:discriminant-ks-operator}:
 Kodaira--Spencer operator on reduced $H^1$
 (\S\ref{sec:master-table}).
\end{itemize}

\smallskip
\noindent\textbf{Physics and BV-BRST.}
\emph{Items marked Heuristic require physics input beyond the algebraic framework.}

\begin{itemize}[nosep]
\item Remark~\ref{rem:bv-equals-bar-cobar}:
 BV formalism equals bar-cobar at all genera
 (Section~\ref{sec:brst-bar-chain-map}).
\item Remark~\ref{rem:quantum-master-complete}:
 Complete quantum master equation from bar-cobar
 (Section~\ref{sec:brst-bar-chain-map}).
\item Conjecture~\ref{conj:v1-bar-cobar-path-integral}:
 Bar-cobar as rigorous path integral
 (Section~\ref{sec:brst-bar-chain-map}).
\item Conjecture~\ref{conj:physical-pairing}:
 Feynman rules dictionary
 (Section~\ref{sec:brst-bar-chain-map}).
\item Conjecture~\ref{conj:string-amplitude}:
 String amplitudes from bar complex
 (Section~\ref{sec:free-field-genera}).
\item Theorem~\ref{thm:modular-anomaly}:
 Modular anomaly equation from bar-cobar
 (Section~\ref{sec:free-field-genera}).
\item Conjecture~\ref{conj:modular-anomaly-brst}:
 Modular anomaly via BRST
 (Section~\ref{sec:free-field-genera}).
\item Theorem~\ref{thm:w-integrability}:
 higher $A_\infty$ correction package for quantum
 $\mathcal{W}$-algebras
 (Section~\ref{sec:free-field-genera}).
\item Conjecture~\ref{conj:v1-bphz-recursion}:
 BPHZ recursion from bar differential
 (Section~\ref{sec:brst-bar-chain-map}).
\end{itemize}

\smallskip
\noindent\textbf{Holomorphic-topological and dualities.}
\begin{itemize}[nosep]
\item Theorem~\ref{thm:en-koszul-duality}:
 $E_n$ Koszul duality from configuration spaces
 (\S\ref{subsec:higher-dim-kd}; proved).

\item Conjecture~\ref{conj:gw-s-duality}:
 Goddard--Witten S-duality from Koszul
 (\S\ref{sec:km-koszul-abstract}).

\item Conjecture~\ref{conj:holographic-koszul-deformation}:
 Holographic duality from deformation quantization
 (\S\ref{sec:km-koszul-abstract}).

\item Conjecture~\ref{conj:deformation-holographic}:
 Deformation quantization = holographic dictionary
 (\S\ref{sec:km-koszul-abstract}).

\item Conjecture~\ref{conj:toroidal-koszul-dual}:
 Toroidal algebra Koszul dual \textup{(}elliptic/double-affine MC4 extension\textup{)}
 (\S\ref{sec:elliptic-bar-heisenberg}).
\item Conjecture~\ref{conj:extended-ferm-ghost}:
 Extended fermion-ghost duality \textup{(}derived/super MC4 extension\textup{)}
 (\S\ref{sec:free-field-genera}).
\item Conjecture~\ref{conj:wrt-conjecture}:
 Chern--Simons/Koszul dictionary for Yangian--quantum affine duality
 (\S\ref{sec:km-koszul-abstract}).
\item Remark~\ref{rem:periodicity-exchange-harmonic}:
 Periodicity--exchange duality
 (\S\ref{sec:km-koszul-abstract}).
\item Conjecture~\ref{conj:superstring-degeneration}:
 Superstring degeneration from genus tower
 (\S\ref{ss:genus}).
\end{itemize}
