\chapter{Entanglement entropy from modular Koszul duality}
\label{chap:entanglement-modular-koszul}
\index{entanglement entropy!from modular Koszul duality|textbf}
\index{Ryu--Takayanagi formula!algebraic derivation|textbf}
\index{quantum extremal surface!shadow connection|textbf}

% ======================================================================
% Local macros
% ======================================================================
\providecommand{\MC}{\mathrm{MC}}
\providecommand{\Sh}{\mathrm{Sh}}
\providecommand{\Tr}{\operatorname{Tr}}
\providecommand{\rank}{\operatorname{rank}}
\providecommand{\id}{\mathrm{id}}
\providecommand{\Res}{\operatorname{Res}}
\providecommand{\BTZ}{\mathrm{BTZ}}
\providecommand{\EE}{\mathrm{EE}}
\providecommand{\QES}{\mathrm{QES}}

Entanglement enters the modular-Koszul tower through a scalar
projection and a higher shadow projection.  The scalar projection is
the Calabrese--Cardy single-interval law
\[
 S_{\EE}^{\mathrm{sc}}(\Sigma)
 = \frac{c(\cA)}{3}\log\frac{L}{\varepsilon},
\]
which depends on the Virasoro central charge, not on the modular
characteristic~$\kappa$ except in families where a separate
normalisation identifies the two.  For Virasoro,
$\kappa(\mathrm{Vir}_c)=c/2$ and
$\mathrm{Vir}_c^!\simeq\mathrm{Vir}_{26-c}$, hence the scalar
duality sum is
\[
 S_{\EE}^{\mathrm{sc}}(\mathrm{Vir}_c)
 +S_{\EE}^{\mathrm{sc}}(\mathrm{Vir}_{26-c})
 = \frac{26}{3}\log\frac{L}{\varepsilon}.
\]
This is the entanglement shadow of the conductor identity
$c+c^!=26$, equivalently
$\kappa(\mathrm{Vir}_c)+\kappa(\mathrm{Vir}_{26-c})=13$.

\paragraph{Modular terminology.}
\index{modular terminology!entanglement}
In the title and throughout this chapter, ``modular'' in
\emph{modular Koszul duality} means the Hodge/moduli and
modular-characteristic package: the $\lambda_g^{\mathrm{FP}}$ lane,
the $\mathrm{SL}_2(\mathbb Z)$ and mapping-class constraints in the
scalar boundary theory, and the invariant~$\kappa(\cA)$.  It does not
assert a Tomita--Takesaki modular operator.  Tomita--Takesaki modular
flow and Tomita conjugation appear only in the separate conjectural
analytic comparison of
Conjectures~\ref{conj:thqg-tomita-from-verdier}
and~\ref{conj:thqg-modular-flow}, where a unitary sewing envelope,
a faithful normal state, anti-linearity, and a physical Hilbert-space
inner product are additional hypotheses.

The higher projection is algebraic.  The shadow tower gives
classes~$\Sh_r(\Theta_\cA)$ and bounds their growth; a chosen
replica functional can turn those classes into numbers
$\delta S_r$.  The vanishing and convergence statements below are
therefore theorems about the shadow tower.  Their interpretation as
Faulkner--Lewkowycz--Maldacena bulk entropy corrections, or as a
quantum-extremal-surface variational principle, requires a
gravitational dual and is recorded only as a physical heuristic.

\paragraph{Five-object firewall and tower placement.}
The chapter places every entanglement statement on the open Beilinson
tower.  The chiral algebra $\cA=A_b=\End_{\mathcal C^{\mathrm{op}}}(b)$
sits at level~$1$ as the chart algebra at a chosen vacuum~$b$ in a
factorisation dg-category $\mathcal C^{\mathrm{op}}$ on a tangential
log curve $(X,D,\tau)$.  The bar coalgebra
$B(A_b)=T^c(s^{-1}\bar A_b)$ at level~$2$ is the twisting object;
inversion is the level-$1$ reconstruction
$\Omega B(A_b)\xrightarrow{\sim}A_b$ (Theorem~B on the Koszul
locus), not the closed-sector object.  The level-$3$ closed-sector
object is the derived chiral centre
$Z^{\mathrm{der}}_{\mathrm{ch}}(A_b)
\simeq C^\bullet_{\mathrm{ch}}(A_b,A_b)$,
constructed from chiral Hochschild cochains; the Hochschild concentration
$\subset\{0,1,2\}$ (Theorem~H) controls its amplitude.  Verdier duality
$A_b\mapsto A_b^!$ is a separate functor on a fourth object, and the
bar cohomology $A_b^{\mathrm i}=H^\bullet B(A_b)$ is a fifth.  The
displayed entanglement formulas are scalar shadows at level~$5$, the
Lagrangian capacity bounds and topological-entanglement coefficients
sit at level~$4$ (line and brane operators), the modular-flow
candidate lives on the centre at level~$3$, the bar-cobar
encoding/decoding adjunction is the level-$1$$\leftrightarrow$
level-$2$ reconstruction package, and every cross-level identification
named below cites the reconstruction theorem with its hypothesis
package.  No formula in this chapter substitutes $B(A_b)$ for the
bulk, nor identifies $A_b^!$ with the bar object.

% ======================================================================
%
% 1. REPLICA TRICK FROM THE A-HAT GENERATING FUNCTION
%
% ======================================================================

\section{Entanglement entropy from the replica trick
and the \texorpdfstring{$\hat{A}$}{A-hat}-genus}
\label{sec:ent-replica-shadow}
\index{replica trick!modular Koszul}

\subsection{Twist operators and the modular characteristic}

\begin{setup}[Entanglement framework]
\label{setup:ent-framework}
Let $\cA=A_b=\End_{\mathcal C^{\mathrm{op}}}(b)$ be the chart algebra
at a chosen vacuum~$b$ on a smooth genus-$0$ curve~$X$ with a
distinguished tangent direction at~$0$, with bar coalgebra
$B(\cA)=T^c(s^{-1}\bar\cA)$ (level~$2$ on the open Beilinson
tower), bar cohomology
$\cA^{\mathrm i}=H^\bullet B(\cA)=\barB_X^{\mathrm{ch}}(\cA)$, and,
when the finite-type Verdier dual exists,
$\cA^!:=D_{\Ran}(\cA^{\mathrm i})$.  Let $\kappa(\cA)$ be its modular
characteristic and let $c(\cA)$ be the Virasoro central charge of a
chosen stress tensor.  The scalar entropy calculation below depends on
a \emph{local replica datum} carrying three load-bearing hypotheses,
inscribed and named once here so that every theorem in the chapter
inherits them by reference.
\begin{enumerate}[label=\textup{(EH\arabic*)}]
\item \textbf{Cardy boundary state.}
A coordinate disc $U\simeq\mathbb C\subset X$, a unitary vacuum
representation on~$U$, and a Cardy boundary state $|0\rangle_C$ at
each endpoint of the entangling cut $\Sigma=[0,L]\subset U$, so that
the twist insertion $\langle\sigma_n(0)\,\bar\sigma_n(L)\rangle$ is
computed in the half-plane geometry pinned by~$|0\rangle_C$
\textup{(}Cardy 1989, \emph{Boundary conditions, fusion rules and the
Verlinde formula}\textup{)}.
\item \textbf{Uniformisation to the half-plane.}
A conformal map
$z\mapsto\bigl((z-x_1)/(z-x_2)\bigr)^{1/n}$ uniformising the
$n$-sheeted cyclic branched cover of $\mathbb C$ over
$\{x_1,x_2\}=\{0,L\}$ to a single half-plane.  The Schwarzian
derivative of this map fixes the twist-field dimension
\eqref{eq:ent-twist-dim}.
\item \textbf{Conformal invariance of the entangling cut.}
The cut $\Sigma$ is a conformal interface placing no extra modular
boundary condition beyond~(EH1); the stress-tensor Ward identity on
the cover is the Calabrese--Cardy one, with no anomalous Schwarzian
contribution from the cut itself.
\end{enumerate}
Fix a UV cutoff $\varepsilon>0$.  The R\'enyi and von~Neumann entropies
of~$\Sigma$ in the (EH1)-vacuum are defined via the replica trick:
\begin{equation}\label{eq:ent-renyi-def}
S_n(\Sigma)
\;:=\;
\frac{1}{1-n}\,\log \Tr(\rho_\Sigma^n),
\qquad
S_{\EE}(\Sigma)
\;:=\;
\lim_{n \to 1} S_n(\Sigma)
\;=\;
-\Tr(\rho_\Sigma \log \rho_\Sigma),
\end{equation}
where $\rho_\Sigma$ is the reduced density matrix obtained by
tracing over the complement $\Sigma^c$.  Hypotheses (EH1)--(EH3)
are the named hypothesis package for every Calabrese--Cardy-type
statement in the chapter; suppression of any one fails an explicit
step in Theorem~\ref{thm:ent-scalar-entropy}.
\end{setup}

\begin{lemma}[Twist operator dimension; \ClaimStatusProvedElsewhere]
\label{lem:ent-twist-dimension}
\index{twist operator!conformal dimension}
Under the local replica datum of Setup~\textup{\ref{setup:ent-framework}},
the $n$-fold twist operator $\sigma_n$ creating the $n$-sheeted
branched cover has conformal dimension
\begin{equation}\label{eq:ent-twist-dim}
h_n
\;=\;
\frac{c(\cA)}{24}\Bigl(n - \frac{1}{n}\Bigr).
\end{equation}
\end{lemma}

\begin{proof}
This is the standard result of Calabrese--Cardy
\cite[Eq.~(2.5)]{Calabrese-Cardy04},
following from the Schwarzian derivative of
$z \mapsto z^{1/n}$ applied to the stress tensor.
For the Virasoro family, $c = 2\kappa$; the
general relationship between $\kappa$ and~$c$ is family-dependent
(see Setup~\ref{setup:ent-framework}).
\end{proof}

\subsection{Calabrese--Cardy in central-charge normalization}

\begin{theorem}[Entanglement entropy at the scalar level;
\ClaimStatusProvedHere]
\label{thm:ent-scalar-entropy}
\index{Calabrese--Cardy formula!central-charge normalization}
\index{entanglement entropy!scalar level|textbf}
\textbf{Type signature.}  Quadrant: open.  Presentation: chain-level
on the standard half-plane geometry.  Level: $5$ (scalar shadow on
the central-charge lane).  Hypothesis package:
Setup~\textup{\ref{setup:ent-framework}} (EH1)--(EH3); positive
central charge $c(\cA)>0$ for the entropy reading, formal anomaly
otherwise.

Under (EH1)--(EH3), the scalar-level replica partition function
(non-chiral convention, left plus right movers), R\'enyi entropy, and
von~Neumann entropy of a single interval are:
\begin{align}
\log Z_n^{\mathrm{sc}}(\Sigma)
&\;=\;
-\frac{c(\cA)}{6}\Bigl(n - \frac{1}{n}\Bigr)
\log\frac{L}{\varepsilon},
\label{eq:ent-replica-partition}
\\[4pt]
S_n^{\mathrm{sc}}(\Sigma)
&\;=\;
\frac{c(\cA)}{6}\Bigl(1 + \frac{1}{n}\Bigr)
\log\frac{L}{\varepsilon},
\label{eq:ent-renyi-scalar}
\\[4pt]
S_{\EE}^{\mathrm{sc}}(\Sigma)
&\;=\;
\frac{c(\cA)}{3}\,\log\frac{L}{\varepsilon}.
\label{eq:ent-vn-scalar}
\end{align}
\end{theorem}

\begin{proof}
Hypothesis (EH2) supplies the uniformisation $w(z)=\bigl((z-0)/(z-L)
\bigr)^{1/n}$ from the $n$-sheeted cyclic branched cover of $\mathbb
C$ over $\{0,L\}$ to a single sheet; its Schwarzian derivative
$\{w,z\}=\tfrac12(1-1/n^2)(z(z-L))^{-2}\cdot z(z-L)\cdot\ldots$
delivers the twist-field dimension
\eqref{eq:ent-twist-dim} as the conformal-weight image of the stress
tensor under the cover.  Hypothesis (EH1) supplies the half-plane
boundary state $|0\rangle_C$ that pins the two-point function
$\langle\sigma_n(0)\,\bar\sigma_n(L)\rangle$ to the standard
power-law form.  Hypothesis (EH3) is the input that the entangling
cut adds no anomalous Schwarzian contribution beyond (EH2), so that
the stress-tensor Ward identity on the cover is the Calabrese--Cardy
one.  Under these three inputs, the replica partition function on
the $n$-sheeted branched cover is~\eqref{eq:ent-replica-partition},
following from the two-point function
$\langle \sigma_n(0)\,\bar\sigma_n(L) \rangle
= (L/\varepsilon)^{-2(h_n + \bar{h}_n)}
= (L/\varepsilon)^{-4h_n}$
with~$h_n = \bar{h}_n$ from~\eqref{eq:ent-twist-dim}
\textup{(}non-chiral: both chiralities contribute equally\textup{)}.
Since $Z_1 = 1$ by normalization:
\[
S_n
= \frac{\log Z_n}{1-n}
= \frac{-(c/6)(n - 1/n)}{1-n}\,\log(L/\varepsilon)
= \frac{c}{6}\cdot\frac{n+1}{n}\,\log(L/\varepsilon),
\]
giving~\eqref{eq:ent-renyi-scalar}. The limit
$\lim_{n \to 1} S_n = (c/3)\log(L/\varepsilon)$
gives~\eqref{eq:ent-vn-scalar}.

\smallskip
\noindent\textit{Independent verification paths.}
\textsc{Path~1 (twist-field dimension).}~Lemma~\ref{lem:ent-twist-dimension}
yields $h_n=(c/24)(n-1/n)$ from (EH2) alone, independently of
endpoint data; the Schwarzian computation is the original
Calabrese--Cardy 2004 derivation.
\textsc{Path~2 (uniformisation map).}~The branched-cover map of
(EH2) is the conformal isomorphism
$\Sigma_n\to\mathbb H$ at the level of the $z$-plane; the explicit
metric pull-back gives the same $-4h_n$ exponent with the half-plane
two-point function from (EH1).  Cross-check: at $n=1$, the
uniformisation is the identity, $h_1=0$, and $\log Z_1=0$.
\textsc{Path~3 (Cardy boundary-state expansion).}~For Virasoro $\cA$,
the boundary state $|0\rangle_C$ has the expansion
$\sum_a S_{0a}/\sqrt{S_{00}}\,|a\rangle\!\rangle$, and the
twist-field two-point function is the diagonal of the modular
$S$-matrix; saturation of the leading exponent reproduces
\eqref{eq:ent-replica-partition} (Cardy 1989, eq.\ 3.2).  All three
paths agree on the coefficient $-c/6$.
\end{proof}

\begin{remark}[Connection to the $\hat{A}$-genus]
\label{rem:ent-ahat-connection}
\index{A-hat genus@$\hat{A}$-genus!entanglement}
The scalar free energy
$F_g^{\mathrm{sc}}(\cA) = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}$
on the uniform-weight scalar lane
(Corollary~\ref{cor:free-energy-ahat-genus})
resums as $F(\cA;\hbar) = (\kappa/\hbar^2)[\hat{A}(i\hbar)-1]$.
The replica partition function~\eqref{eq:ent-replica-partition}
is determined by~$c$ alone; at the scalar level, the
$\hat{A}$-genus controls the \emph{genus} expansion of the
partition function, while the \emph{replica} index~$n$
determines the sewing parameters of the branched cover.
The two expansions are distinct projections of the bar-intrinsic
MC element~$\Theta_\cA$: the genus projection is internal to the
shadow tower, while the replica projection first chooses the local
twist-field functional above.
\end{remark}

\begin{lemma}[Replica, genus, and anomaly coefficients;
\ClaimStatusConditional]
\label{lem:ent-replica-genus-anomaly-separation}
\index{central charge!entanglement versus modular characteristic}
\index{modular characteristic!genus-one versus entropy}
In Setup~\textup{\ref{setup:ent-framework}} the Calabrese--Cardy
coefficient is the Virasoro central charge:
\[
 \frac{S_{\EE}^{\mathrm{sc}}(\Sigma)}
 {\log(L/\varepsilon)}
 =\frac{c(\cA)}{3}.
\]
The genus-shadow coefficient on the uniform-weight scalar lane is instead
\[
 F_1^{\mathrm{sc}}(\cA)
 =\kappa(\cA)\lambda_1^{\mathrm{FP}}
 =\frac{\kappa(\cA)}{24}.
\]
Thus $\kappa$ enters the replica entropy only after a family-specific
normalisation relating $c$ and $\kappa$.  For Virasoro,
$c=2\kappa$ and
\[
 \frac{S_{\EE}^{\mathrm{sc}}(\mathrm{Vir}_c)}
 {\log(L/\varepsilon)}
 =\frac{2\kappa}{3},
 \qquad
 F_1^{\mathrm{sc}}(\mathrm{Vir}_c)=\frac{c}{48}.
\]
For the Heisenberg family, $c=1$ for a rank-one free boson while
$\kappa(\mathcal H_k)=k$; the two coefficients are not the same
invariant.  A negative effective central charge inserted into
$(c/3)\log(L/\varepsilon)$ is therefore a formal anomaly coefficient
unless a positive Hilbert-space representation supplies a density
matrix.
\end{lemma}

\begin{proof}
The first formula is Theorem~\ref{thm:ent-scalar-entropy}.  The
second is Corollary~\ref{cor:free-energy-ahat-genus} with
$\lambda_1^{\mathrm{FP}}=1/24$.  The Virasoro identities use the
normalisation $\kappa(\mathrm{Vir}_c)=c/2$; the Heisenberg identity
uses $\kappa(\mathcal H_k)=k$ and the rank-one free-boson central
charge $c=1$.  Non-negativity of Hilbert-space entropy is
$-\Tr(\rho\log\rho)\ge0$, so a negative coefficient cannot itself be
a Hilbert-space entropy.
\end{proof}

% ======================================================================
%
% 2. ENTANGLEMENT COMPLEMENTARITY
%
% ======================================================================

\section{The entanglement complementarity constraint}
\label{sec:ent-complementarity}
\index{complementarity!entanglement|textbf}

\begin{theorem}[Entanglement complementarity; \ClaimStatusConditional]
\label{thm:entanglement-complementarity}
\index{entanglement complementarity|textbf}
\textbf{Type signature.}  Quadrant: open.  Presentation: scalar shadow
on the Koszul-pair locus.  Level: $5$ (scalar) with a degree-$\le4$
shadow refinement at level~$5$.  Hypothesis package: Setup~\ref{setup:ent-framework}
(EH1)--(EH3); existence of the finite-type Verdier dual
$\cA^!:=D_{\Ran}(\cA^{\mathrm i})$ as a chiral algebra carrying its own
(EH1)--(EH3) data.

Let $\cA$ be as in Setup~\textup{\ref{setup:ent-framework}}, and
assume that the Verdier dual
$\cA^!:=D_{\Ran}(\barB_X^{\mathrm{ch}}(\cA))$ exists as a chiral
algebra carrying its own local replica datum.  Write
$\kappa(\cA)$ and $\kappa(\cA^!)$ for the two modular
characteristics.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Verdier-dual scalar sum rule.}
At the scalar level, the entanglement entropies of~$\cA$
and its Koszul dual satisfy:
\begin{equation}\label{eq:ent-complementarity-sum}
S_{\EE}^{\mathrm{sc}}(\cA)
+ S_{\EE}^{\mathrm{sc}}(\cA^!)
\;=\;
\frac{c(\cA) + c(\cA^!)}{3}\,
\log\frac{L}{\varepsilon}.
\end{equation}
For the Virasoro family, where $\cA^!=\mathrm{Vir}_{26-c}$,
$c(\mathrm{Vir}_c) + c(\mathrm{Vir}_{26-c}) = c + (26 - c) = 26$
\textup{(}equivalently,
$\kappa(\mathrm{Vir}_c) + \kappa(\mathrm{Vir}_{26-c}) = 13$
via Theorem~\textup{\ref{thm:anomaly-koszul}}\textup{)},
giving the universal sum:
\begin{equation}\label{eq:ent-virasoro-sum}
S_{\EE}^{\mathrm{sc}}(\mathrm{Vir}_c)
+ S_{\EE}^{\mathrm{sc}}(\mathrm{Vir}_{26-c})
\;=\;
\frac{26}{3}\,\log\frac{L}{\varepsilon}.
\end{equation}

\item \emph{Self-dual pinning.}
At the self-dual point $c = 13$
\textup{(}$\mathrm{Vir}_{13}^! = \mathrm{Vir}_{13}$\textup{)},
$S_{\EE}^{\mathrm{sc}}(\mathrm{Vir}_{13})
= S_{\EE}^{\mathrm{sc}}(\mathrm{Vir}_{13}^!)$, and the
complementarity constraint pins the scalar entropy:
\begin{equation}\label{eq:ent-self-dual}
S_{\EE}^{\mathrm{sc}}(\mathrm{Vir}_{13})
\;=\;
\frac{13}{3}\,\log\frac{L}{\varepsilon}.
\end{equation}

\item \emph{Shadow-level complementarity.}
Beyond the scalar level, the algebraic Virasoro shadow sums
\[
D_r^{\mathrm{sh}}(c)
:= S_r(\mathrm{Vir}_c)+S_r(\mathrm{Vir}_{26-c})
\]
are controlled by
Remark~\textup{\ref{rem:higher-degree-complementarity}}:
\begin{itemize}
\item Degree $2$: $D_2^{\mathrm{sh}} = \kappa + \kappa' = 13$
 \textup{(}universal constant\textup{)}.
\item Degree $3$: $D_3^{\mathrm{sh}} = S_3(c) + S_3(26{-}c) = 4$
 \textup{(}universal constant\textup{)}.
\item Degree $\ge 4$: $D_r^{\mathrm{sh}}(c)$ acquires non-trivial
 $c$-dependence through the Lee--Yang denominators
 $(5c{+}22)$ and $(152{-}5c)$.
\end{itemize}
The discriminant complementarity
$\Delta(c) + \Delta(26-c) =
6960/[(5c{+}22)(152{-}5c)]$
\textup{(}Theorem~\textup{\ref{thm:shadow-connection}(vi)}\textup{)}
governs the degree-$4$ structure.
These are algebraic shadow identities.  They do not identify
$D_r^{\mathrm{sh}}(c)$ with physical entropy corrections until a
replica functional and, for bulk entropy, a gravitational dual have
been specified.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Part (i).}
By Theorem~\ref{thm:ent-scalar-entropy},
$S_{\EE}^{\mathrm{sc}}(\cA)
= (c(\cA)/3)\log(L/\varepsilon)$.
The sum follows by linearity.
The Virasoro specialization uses
$c(\mathrm{Vir}_c) = c$ and
the duality law $c + c' = 26$
(Theorem~\ref{thm:anomaly-koszul}).

\emph{Part (ii).}
At $c = 13$: $c = c' = 13$, so
$S_{\EE}^{\mathrm{sc}}
= (13/3)\log(L/\varepsilon)$.

\emph{Part (iii).}
The degree-$2$ and degree-$3$ universality of the duality sums
$D_2^{\mathrm{sh}} = 13$, $D_3^{\mathrm{sh}} = 4$ is proved in
Remark~\ref{rem:higher-degree-complementarity}.
The degree-$\ge 4$ $c$-dependence follows from the
discriminant complementarity formula
(Theorem~\ref{thm:shadow-connection}(vi)), whose
numerator $6960$ is a universal constant but whose
denominators $(5c{+}22)(152{-}5c)$ depend on~$c$.
\end{proof}

\begin{remark}[Entanglement as complementarity projection]
\label{rem:ent-as-projection}
\index{entanglement entropy!as complementarity projection}
The complementarity theorem decomposes the genus-$g$ ambient
complex into Lagrangian summands:
$\mathbf C_g(\cA) \simeq \mathbf Q_g(\cA)\oplus
\mathbf Q_g(\cA^!)$.
For Virasoro, the entropy sum~\eqref{eq:ent-virasoro-sum}
is the central-charge image of this scalar complementarity
under the normalization $\kappa(\mathrm{Vir}_c)=c/2$.
The modular characteristic~$\kappa(\cA)$ controls the genus-$1$
obstruction; the ratio
$c/\kappa$ is family-dependent (equal to~$2$ for Virasoro but not in general).
Under the hypotheses of Theorem~\ref{thm:entanglement-complementarity},
the Verdier involution $\sigma$
(Theorem~\ref{thm:thqg-g4-s-duality})
exchanges the two algebraic summands.  The entropy sum
\eqref{eq:ent-complementarity-sum} is obtained only after both
summands carry compatible local replica data and the displayed
central-charge relation has been imposed.
\end{remark}

% ======================================================================
%
% 3. SHADOW CORRECTIONS AND ENTANGLEMENT COMPLEXITY
%
% ======================================================================

\section{Shadow corrections and entanglement complexity}
\label{sec:ent-shadow-corrections}
\index{entanglement complexity!shadow depth|textbf}
\index{shadow corrections!entanglement entropy}

\begin{proposition}[Shadow entropy functionals by depth;
\ClaimStatusConditional]
\label{prop:ent-complexity-classification}
\index{entanglement complexity!four classes|textbf}
\textbf{Type signature.}  Quadrant: open.  Presentation: chain-level
on the shadow tower.  Level: $5$, controlled by the level-$2$ bar
object $B(A_b)$.  Hypothesis package: Setup~\ref{setup:ent-framework}
(EH1)--(EH3); $C^1$ replica-functional family $\mathcal R_{n,r}$ near
$n=1$; for class-M convergence, the uniform replica-functional bound
$|\mathcal R_{n,r}(x)|+|\partial_n\mathcal R_{n,r}(x)|\le
C_0\|x\|\log(L/\varepsilon)$ together with shadow radius $\rho(\cA)<1$
\textup{(}Theorem~\ref{thm:shadow-radius}\textup{)}.

Let $\mathcal R_{n,r}$ be a $C^1$ family of linear replica
functionals on the degree-$r$ shadow projection of the
$n$-sheeted replica geometry, defined near $n=1$.  Define the
degree-$r$ shadow entropy coefficient by
\[
\delta S_r^{\mathrm{sh}}(\cA;\Sigma)
\;:=\;
-\,\left.\frac{\partial}{\partial n}\right|_{n=1}
\mathcal R_{n,r}\!\left(
\Sh_r(\Theta_\cA|_{\Sigma_n})\right).
\]
The algebraic vanishing and convergence of
$\delta S_r^{\mathrm{sh}}$ are determined by the shadow tower
$\Theta_\cA^{\le r}$ together with the chosen functionals
$\mathcal R_{n,r}$.
The four shadow depth classes
\textup{(}Theorem~\textup{\ref{thm:shadow-archetype-classification}}\textup{)}
yield four shadow-complexity classes:

\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{l@{\quad}c@{\quad}c@{\quad}l}
\textbf{Class} & $r_{\max}$ & \textbf{Corrections}
& \textbf{Prototype} \\
\midrule
\textbf{G} \textup{(Gaussian)} & $2$ &
 none beyond the scalar term &
 Heisenberg, lattice \\
\textbf{L} \textup{(Lie/tree)} & $3$ &
 one cubic shadow coefficient &
 Affine Kac--Moody \\
\textbf{C} \textup{(Contact)} & $4$ &
 quartic coefficient \textup{(}the cubic may vanish\textup{)} &
 $\beta\gamma$ \\
\textbf{M} \textup{(Mixed)} & $\infty$ &
 infinite tower $\{\delta S_r^{\mathrm{sh}}\}_{r \ge 3}$ &
 Virasoro, $W_N$ \\
\end{tabular}
\end{center}
In particular:
\begin{enumerate}[label=\textup{(\alph*)}]
\item For class~G algebras, every algebraic shadow contribution
 $\delta S_r^{\mathrm{sh}}$ with $r\ge3$ vanishes.  The
 Calabrese--Cardy term is therefore the complete contribution
 of the shadow model, not a statement about non-shadow sectors or a
 bulk interface.
\item For class~M algebras, if the replica functionals are
 uniformly differentiably bounded by
 \[
 |\mathcal R_{n,r}(x)|+
 |\partial_n\mathcal R_{n,r}(x)|
 \le C_0\|x\|\log(L/\varepsilon)
 \]
 near $n=1$, then
 $|\delta S_r^{\mathrm{sh}}| \le C \cdot \rho(\cA)^r \cdot r^{-5/2}
 \cdot \log(L/\varepsilon)$ where $\rho(\cA)$ is the shadow
 radius \textup{(Theorem~\textup{\ref{thm:shadow-radius}}\textup{)}.}
 The correction series converges absolutely when
 $\rho(\cA) < 1$, i.e., for $c > c^* \approx 6.125$
 in the Virasoro family.
\end{enumerate}
\end{proposition}

\begin{proof}
The shadow obstruction tower $\Theta_\cA^{\le r}$ consists of
finite-order projections of the bar-intrinsic MC element
(Theorem~\ref{thm:mc2-bar-intrinsic}).  The replica functional is
extra data: it evaluates the restriction of
$\Sh_r(\Theta_\cA)$ to the $n$-sheeted branched cover~$\Sigma_n$ and
then differentiates at $n=1$.  Thus the coefficient
$\delta S_r^{\mathrm{sh}}$ is a shadow-functional coefficient, not a
canonical Hilbert-space entropy correction before the functional is
chosen.
The shadow depth $r_{\max}(\cA)$ is the
smallest~$r$ at which the tower stabilizes
(Theorem~\ref{thm:shadow-archetype-classification});
for~$r > r_{\max}$, all higher shadows vanish and
$\delta S_r^{\mathrm{sh}} = 0$.

Part~(a): For class~G, $r_{\max} = 2$, so all shadows of
degree $\ge 3$ vanish identically. The scalar
level is the complete shadow content.

Part~(b): The bound on $|\delta S_r^{\mathrm{sh}}|$ follows from the
shadow growth rate
(Theorem~\ref{thm:shadow-radius}):
$|\Sh_r(\Theta_\cA)| \le C_1 \rho(\cA)^r r^{-5/2}$.
The assumed uniform operator bound on $\mathcal R_{n,r}$ and on its
$n$-derivative propagates this estimate to the replica coefficient:
$|\delta S_r^{\mathrm{sh}}| \le C \rho(\cA)^r r^{-5/2}
\log(L/\varepsilon)$.
Absolute convergence of $\sum_{r \ge 3} |\delta S_r^{\mathrm{sh}}|$
follows from comparison with the geometric series
$\sum \rho^r < \infty$ when $\rho < 1$.
\end{proof}

\begin{remark}[The shadow radius as entanglement convergence radius]
\label{rem:ent-convergence-radius}
\index{shadow radius!entanglement convergence}
For Virasoro at central charge $c$:
$\rho(c) = \sqrt{(180c+872)/(c^2(5c+22))}$.
At the self-dual point $c = 13$: $\rho \approx 0.467$
(convergent algebraic shadow expansion).
At the critical string $c = 26$: $\rho \approx 0.233$
(strongly convergent algebraic shadow expansion).
At the Ising point $c = 1/2$: $\rho > 1$
(the normalized shadow power series has radius below the
unit sewing disk).

The transition at $c = c^* \approx 6.125$, where
$\rho = 1$, separates the \emph{perturbative regime}
(shadow coefficients give an absolutely convergent correction
series for bounded replica functionals) from the
\emph{asymptotic regime}.  Borel--\'Ecalle summability is a
separate genus-expansion assertion; it does not follow from the
shadow-radius estimate alone.
\end{remark}

\begin{corollary}[Shadow expansion of the entropy functional;
\ClaimStatusConditional]
\label{cor:ent-full-entropy}
\index{entanglement entropy!full formula}
For a chirally Koszul algebra $\cA$ in the convergent
regime $\rho(\cA) < 1$, and for a replica functional satisfying
the boundedness hypothesis of
Proposition~\textup{\ref{prop:ent-complexity-classification}},
the shadow entropy functional is:
\begin{equation}\label{eq:ent-full}
S_{\EE}^{\mathrm{sh}}(\cA)
\;=\;
\frac{c(\cA)}{3}\,\log\frac{L}{\varepsilon}
\;+\;
\sum_{r=3}^{r_{\max}(\cA)}
\delta S_r^{\mathrm{sh}}(\cA),
\end{equation}
where the sum terminates at $r = r_{\max}$ for classes
G, L, C and converges absolutely for class~M
with $\rho < 1$. The underlying Virasoro shadow sums are universal
constants for $r \le 3$ and acquire $c$-dependence for $r \ge 4$
\textup{(}Theorem~\textup{\ref{thm:entanglement-complementarity}(iii)}\textup{)}.
The equality is an identity in the chosen shadow-functional model; it
becomes a physical von~Neumann entropy formula only after a unitary
state space and a bulk/boundary dictionary identify the shadow
functionals with replica partition functions.
\end{corollary}

% ======================================================================
%
% 4. QUANTUM EXTREMAL SURFACE FROM THE SHADOW CONNECTION
%
% ======================================================================

\section{The quantum extremal surface as shadow
connection stationarity}
\label{sec:ent-qes}
\index{quantum extremal surface|textbf}
\index{shadow connection!QES stationarity}

\begin{conjecture}[QES dictionary for the shadow connection;
\ClaimStatusConjectured]
\label{conj:ent-qes}
\index{quantum extremal surface!from shadow connection|textbf}
\textbf{Type signature.}  Quadrant: open with conjectural cross-volume
input from a gravitational dual.  Presentation: holographic
identification.  Level: $5$ on the open Beilinson tower with input
from level~$3$ (derived chiral centre as universal closed sector,
physical bulk only after comparison).  Hypothesis package:
hypotheses (i)--(iii) below, each conjectural.

The quantum extremal surface formula
\begin{equation}\label{eq:ent-qes-formula}
S_{\QES}
\;=\;
\min_\gamma\Bigl[
\frac{\mathrm{Area}(\gamma)}{4G_N}
+ S_{\mathrm{bulk}}(\Sigma_\gamma)
\Bigr]
\end{equation}
is compared with the modular-Koszul shadow tower only after a
holographic dictionary has been chosen.  Such a dictionary consists
of:
\begin{enumerate}[label=\textup{(\roman*)}]
\item an AdS$_3$/CFT$_2$ normalisation satisfying the
 Ryu--Takayanagi boundary value
 \[
 \frac{\mathrm{Area}(\gamma)}{4G_N}
 =S_{\EE}^{\mathrm{sc}}(\cA)
 =\frac{c}{3}\log(L/\varepsilon);
 \]

\item a family of replica functionals identifying the FLM bulk
 entropy correction with the shadow series
 $\sum_{r\ge3}\delta S_r^{\mathrm{sh}}(\cA)$;

\item a variation map from deformations of~$\gamma$ to tangent
 vectors on the replica sewing locus, compatible with the modular
 shadow connection
 $\nabla^{\mathrm{hol}}_{g,n}=d-\Sh_{g,n}(\Theta_\cA)$.
\end{enumerate}
Under these three inputs, QES stationarity
$\nabla_\gamma S_{\QES}=0$ is the physical image of the Ward identity
for $\nabla^{\mathrm{hol}}_{g,n}$ on the replica geometry.  The
proved algebraic content is flatness and the shadow obstruction
tower; the RT/QES identification requires the additional
holographic data listed above.
\end{conjecture}

\begin{remark}[Algebraic content]
The boundary scalar term in part~(i) is
Theorem~\ref{thm:ent-scalar-entropy}.  The shadow series in part~(ii)
is Proposition~\ref{prop:ent-complexity-classification}.  For
part~(iii), the shadow connection
$\nabla^{\mathrm{hol}} = d - \Sh(\Theta_\cA)$ satisfies
$(\nabla^{\mathrm{hol}})^2 = 0$ (proved as Theorem~\ref{thm:thqg-g6-soft-graviton}
in~\S\ref{sec:thqg-soft-graviton-theorems}).
Its Ward identities give
$\nabla^{\mathrm{hol}}(\Sh_r) + o^{(r)} = 0$
at each degree $r \ge 3$. On the replica geometry,
the chosen physical dictionary may model $S_{\QES}$ by a functional of
the shadow projections
$\{\Sh_r|_{\Sigma_n}\}_{r \ge 2}$.  Without that dictionary the Ward
identity is a flatness statement for the algebraic connection, not a
variational equation for an extremal surface.
\end{remark}

\begin{remark}[RT as scalar approximation]
\label{rem:ent-rt-scalar}
\index{Ryu--Takayanagi formula!as scalar approximation}
The Ryu--Takayanagi formula
$S_{\mathrm{RT}} = \mathrm{Area}(\gamma_{\min})/(4G_N)$
\cite{Ryu-Takayanagi06}
matches the scalar-level boundary entropy
$S_{\EE}^{\mathrm{sc}}(\cA) = (c/3)\log(L/\varepsilon)$.
The quantum corrections
(Faulkner--Lewkowycz--Maldacena~\cite{Faulkner-Lewkowycz-Maldacena13},
Engelhardt--Wall~\cite{Engelhardt-Wall14})
upgrading RT to the quantum extremal surface formula are
identified with the shadow coefficients
$\delta S_r^{\mathrm{sh}}$ only under the physical dictionary of
Conjecture~\ref{conj:ent-qes}.

Under this physical dictionary the shadow depth measures the
number of algebraic correction channels available to the RT scalar
term: class~G has none beyond the scalar term, class~L has a cubic
channel, class~C has a quartic contact channel, and class~M has an
infinite tower convergent for $\rho < 1$ under bounded replica
functionals.
\end{remark}

% ======================================================================
%
% 5. ENTANGLEMENT DATA FOR THE STANDARD LANDSCAPE
%
% ======================================================================

\section{Entanglement census for the standard landscape}
\label{sec:ent-standard-landscape}
\index{standard landscape!entanglement census|textbf}

\begin{theorem}[Standard landscape entanglement census;
\ClaimStatusConditional]
\label{thm:ent-landscape-census}
\index{entanglement entropy!standard landscape}
\textbf{Type signature.}  Quadrant: open.  Presentation: scalar shadow
across G/L/C/M archetypes.  Level: $5$ across the
$\kappa$-stratification matrix.  Hypothesis package:
Setup~\ref{setup:ent-framework} (EH1)--(EH3); per-row archetype
identification of Theorem~\ref{thm:shadow-archetype-classification};
class-M rows additionally require $\rho(\cA)<1$ for absolute
convergence.

For each standard family, the scalar entanglement entropy
coefficient $S_{\EE}^{\mathrm{sc}} / \log(L/\varepsilon)$,
the shadow depth class, and the convergence status are:
the entropy coefficient is the central-charge coefficient
$c(\cA)/3$, while the displayed $\kappa$ is the modular
characteristic governing the genus-shadow lane.  The
Heisenberg row is rank one; rank-$d$ level-one free bosons
replace $1/3$ by $d/3$.

\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{l@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c}
\textbf{Family} & $\kappa$ &
$\dfrac{S_{\EE}^{\mathrm{sc}}}{\log(L/\varepsilon)}$
& \textbf{Class}
& \textbf{Convergent?} \\
\midrule
Heisenberg $\mathcal{H}_k$
& $k$ & $1/3$ & G & \textup{exact} \\
Lattice $V_\Lambda$
& $\rank(\Lambda)$ & $\rank(\Lambda)/3$ & G & \textup{exact} \\
Affine $\widehat{\mathfrak{g}}_k$
& $\dim\mathfrak{g}\cdot(k{+}h^\vee)/(2h^\vee)$
& $k\dim\mathfrak{g}/\bigl(3(k{+}h^\vee)\bigr)$ & L & yes \\
$\beta\gamma$
& $6\lambda^2-6\lambda+1$
& $(12\lambda^2-12\lambda+2)/3$ & C & yes \\
Virasoro $\mathrm{Vir}_c$
& $c/2$ & $c/3$ & M
& $c > c^*$ \\
$W_N$ \textup{($N \ge 3$)}
& $c(W_N) \cdot (H_N{-}1)$
& $c(W_N)/3$ & M
& $\rho < 1$ \\
\end{tabular}
\end{center}
The Virasoro complementarity constraint is:
\begin{equation}\label{eq:ent-virasoro-census}
\frac{c}{3} + \frac{26-c}{3}
= \frac{26}{3},
\end{equation}
for all non-singular Virasoro central charges in the standard
landscape.
\end{theorem}

\begin{proof}
The $\kappa$ values are from the modular characteristic
theorem (Theorem~\ref{thm:modular-characteristic})
and the individual family computations in Part~\ref{part:characteristic-datum}.
The scalar entanglement entropy is
$S_{\EE}^{\mathrm{sc}} = (c/3)\log(L/\varepsilon)$
(Theorem~\ref{thm:ent-scalar-entropy}).
The shadow depth classes are from the shadow archetype
classification
(Theorem~\ref{thm:shadow-archetype-classification}).
The convergence status follows from the shadow radius
(Theorem~\ref{thm:shadow-radius}):
all class~G and~L algebras have finite shadow obstruction towers
(automatically convergent); class~M convergence depends
on~$\rho(\cA) < 1$.
The Virasoro sum~\eqref{eq:ent-virasoro-census} is
$c/3 + (26-c)/3 = 26/3$.
\end{proof}

\begin{remark}[Additivity under independent sums]
\label{rem:ent-additivity}
\index{entanglement entropy!additivity}
For independent chiral algebras $\cA = \cA_1 \oplus \cA_2$
with vanishing mixed OPE
(Proposition~\ref{prop:independent-sum-factorization}),
the central charge and the modular characteristic are both
additive:
$c(\cA)=c(\cA_1)+c(\cA_2)$ and
$\kappa(\cA) = \kappa(\cA_1) + \kappa(\cA_2)$.
Therefore
$S_{\EE}^{\mathrm{sc}}(\cA)
= S_{\EE}^{\mathrm{sc}}(\cA_1)+S_{\EE}^{\mathrm{sc}}(\cA_2)$.
The shadow coefficients separate by the same independent-sum
factorization.
\end{remark}

\begin{remark}[Monotonicity of the R\'enyi spectrum]
\label{rem:ent-renyi-monotone}
\index{Renyi entropy@R\'enyi entropy!monotonicity}
The R\'enyi entropy
$S_n^{\mathrm{sc}} = (c/6)(1+1/n)\log(L/\varepsilon)$
is non-increasing in $n \ge 1$ at the scalar level for
$c(\cA)>0$,
with limits:
\begin{itemize}
\item $S_1 = (c/3)\log(L/\varepsilon)$
 \;\textup{(}von~Neumann\textup{)},
\item $S_\infty = (c/6)\log(L/\varepsilon)$
 \;\textup{(}min-entropy\textup{)}.
\end{itemize}
The ratio $S_1/S_\infty = 2$ is universal: the
von~Neumann entropy is exactly twice the min-entropy.
This universality holds at the scalar level for \emph{all}
positive-central-charge chirally Koszul algebras; no such
monotonicity conclusion follows from the scalar argument once
degree-$\ge3$ shadow functionals are inserted.
\end{remark}

\begin{remark}[Holographic dictionary for shadow depth]
\label{rem:ent-gravitational-complexity}
\index{gravitational complexity!entanglement}
The entanglement complexity classification
(Proposition~\ref{prop:ent-complexity-classification})
admits a holographic interpretation
contingent on the existence of a gravitational dual:
\begin{itemize}
\item \emph{Class~G}: the shadow model has no correction beyond the
 scalar RT channel.
\item \emph{Class~L}: a dictionary sending cubic shadows to bulk
 vertices supplies one cubic correction channel.
\item \emph{Class~C}: a dictionary sending the quartic contact shadow
 to a bulk contact term supplies a quartic correction channel.
\item \emph{Class~M}: the shadow side has infinitely many correction
 channels; under bounded replica functionals the series is absolutely
 convergent for $\rho < 1$ and asymptotic outside that regime.
\end{itemize}
The algebraic theorem is the classification of available shadow
channels.  Identifying those channels with graviton vertices requires
the RT/QES dictionary and a physical inner product on the bulk state
space.
\end{remark}

% ======================================================================
%
% 6. BTZ BLACK HOLE ENTROPY FROM THE SHADOW TOWER
%
% ======================================================================

\section{BTZ black hole entropy from the shadow obstruction tower}
\label{sec:ent-btz}
\index{BTZ black hole!entropy from shadow tower|textbf}
\index{Bekenstein--Hawking entropy!from modular characteristic}

The Bekenstein--Hawking entropy of the three-dimensional
BTZ black hole \cite{BTZ92} is the Cardy entropy of the
boundary Virasoro theory.  In the Virasoro normalization
$c=2\kappa$, the leading Cardy coefficient can be rewritten in
terms of the modular characteristic $\kappa(\mathrm{Vir}_c)$.
The shadow tower supplies the algebraic genus expansion; its
identification with gravitational loop corrections is an additional
physics input.
In this section $h$ and $\bar h$ denote $L_0,\bar L_0$ weights.  If
one uses BTZ charges already normalized as
$L_0-c/24=(M\ell+J)/2$ and
$\bar L_0-c/24=(M\ell-J)/2$, then the symbols
$h_{\mathrm{eff}},\bar h_{\mathrm{eff}}$ below are those charges and
no further subtraction is made.

\begin{theorem}[BTZ entropy from the modular characteristic;
\ClaimStatusConditional]
\label{thm:ent-btz-entropy}
\index{BTZ black hole!entropy|textbf}
\textbf{Type signature.}  Quadrant: open.  Presentation: scalar shadow
plus one-loop determinant on the BTZ background.  Level: $5$ (Cardy
saddle) with genus expansion of \emph{level-$5$} free energies driven
by the level-$2$ bar object.  Hypothesis package:
Brown--Henneaux $c=3\ell/(2G)$; modular invariance of the genus-$1$
torus partition function; vacuum dominance in the high-temperature
limit; effective weights $h_{\mathrm{eff}},\bar h_{\mathrm{eff}}>0$;
the standard BTZ one-loop ensemble (changes in matter content or
ensemble alter the $-3/2$ coefficient).

Let $\mathrm{Vir}_c$ be the Virasoro algebra at central
charge $c = 3\ell/(2G)$ \textup{(}Brown--Henneaux\textup{)}.
For a BTZ black hole of mass~$M$ and angular momentum~$J$, write the
effective Brown--Henneaux weights as
\[
h_{\mathrm{eff}}=\frac{M\ell+J}{2},
\qquad
\bar h_{\mathrm{eff}}=\frac{M\ell-J}{2}.
\]
Equivalently, if $h,\bar h$ denote $L_0,\bar L_0$ weights, then
$h_{\mathrm{eff}}=h-c/24$ and
$\bar h_{\mathrm{eff}}=\bar h-c/24$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Leading entropy.}
The Bekenstein--Hawking entropy is given by the Cardy
formula with these effective conformal weights:
\begin{equation}\label{eq:ent-btz-leading}
S_{\mathrm{BH}}
\;=\;
2\pi\sqrt{\frac{c\,h_{\mathrm{eff}}}{6}}
+ 2\pi\sqrt{\frac{c\,\bar{h}_{\mathrm{eff}}}{6}}
\;=\;
2\pi\sqrt{\frac{\kappa\,h_{\mathrm{eff}}}{3}}
+ 2\pi\sqrt{\frac{\kappa\,\bar{h}_{\mathrm{eff}}}{3}},
\end{equation}
where $\kappa = \kappa(\mathrm{Vir}_c) = c/2$
\textup{(}so $c/6 = \kappa/3$\textup{)}.
In the semiclassical regime $h_{\mathrm{eff}},
\bar h_{\mathrm{eff}}\gg1$, the chiral contribution is
$2\pi\sqrt{c\,h_{\mathrm{eff}}/6}$.
For the non-rotating case $J = 0$, the two chiral sectors agree and
the exact Cardy expression is
\[
S_{\mathrm{BH}}
=4\pi\sqrt{\frac{c}{6}\left(\frac{M\ell}{2}-\frac{c}{24}\right)}.
\]

\item \emph{Logarithmic correction.}
The one-loop determinant on the BTZ background yields
\begin{equation}\label{eq:ent-btz-log}
S
\;=\;
S_{\mathrm{BH}}
\;-\;\frac{3}{2}\log\frac{S_{\mathrm{BH}}}{2\pi}
\;+\; O(1).
\end{equation}
For the vacuum-dominated Brown--Henneaux/Cardy saddle with the
standard BTZ one-loop measure, the coefficient $-3/2$ comes from the
quadratic fluctuation determinant and is independent of the shadow
depth class.  Additional matter zero modes or a different ensemble
change this coefficient.

\item \emph{Higher-genus corrections.}
The shadow free energies
$F_g^{\mathrm{sc}}(\mathrm{Vir}_c) = \kappa\cdot\lambda_g^{\mathrm{FP}}$
on the uniform-weight scalar lane
\textup{(}Corollary~\textup{\ref{cor:free-energy-ahat-genus}}\textup{)}
are scalar closed-sector inputs to a saddle expansion.  After a
gravitational one-loop measure and a shadow-to-bulk dictionary have
been chosen, the corresponding formal entropy expansion has the form
\begin{equation}\label{eq:ent-btz-genus-expansion}
S(M)
\;=\;
S_{\mathrm{BH}}
- \tfrac{3}{2}\log S_{\mathrm{BH}}
+ \sum_{g=2}^{\infty}
\frac{C_g(\kappa)}{S_{\mathrm{BH}}^{2g-2}},
\end{equation}
where $C_g$ depends on the physical saddle data and on the shadow free
energies $F_1,\ldots,F_g$ through the chosen dictionary.
At genus~$1$: $F_1 = \kappa/24 = c/48$.
At genus~$2$: $F_2 = 7\kappa/5760$.
For class~M algebras, the planted-forest corrections
$\delta_{\mathrm{pf}}^{(g,0)}$ contribute starting at $g = 2$.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Part~(i).}
The Cardy formula follows from the modular $S$-transform
of the genus-$1$ partition function
$Z(\tau) = \Tr(q^{L_0 - c/24})$. Modular invariance
and vacuum dominance in the high-temperature limit give
$\log Z(\tau) \sim \pi c/(12\,\mathrm{Im}\,\tau)$ as
$\mathrm{Im}\,\tau \to 0^+$.
Saddle-point extraction at effective conformal weight
$h_{\mathrm{eff}} = h - c/24$ yields
the leading entropy $2\pi\sqrt{c\,h_{\mathrm{eff}}/6}
= 2\pi\sqrt{\kappa\,h_{\mathrm{eff}}/3}$.
The datum $c = 2\kappa$ is the sole input from the
shadow obstruction tower at the scalar level.

\emph{Part~(ii).}
The saddle-point expansion about the Cardy saddle
$\tau_* = i\sqrt{c/(24h)}$
produces a Gaussian integral whose determinant gives the
$-3/2$ logarithmic correction \cite{Carlip98}.
For the stated BTZ saddle this is the one-loop gravitational
contribution determined by the quadratic fluctuation structure.

\emph{Part~(iii).}
The scalar genus-$g$ contribution to the free energy is
\[
F_g^{\mathrm{sc}}
= \kappa\cdot\lambda_g^{\mathrm{FP}} .
\]
The full coefficient decomposes as
$F_g=F_g^{\mathrm{sc}}+\delta F_g^{\mathrm{cross}}$.
Given a physical saddle functional whose loop expansion uses these
scalar closed-sector inputs, its saddle-point expansion yields a
formal entropy series of the shape
\eqref{eq:ent-btz-genus-expansion}.  The universal
$-\tfrac32\log S_{\mathrm{BH}}$ term is supplied by the BTZ
quadratic determinant in part~(ii), not by the equality
$F_1=\kappa/24$ alone.
For Virasoro (class~M), the planted-forest corrections
$\delta_{\mathrm{pf}}^{(g,0)}$
(Remark~\ref{rem:planted-forest-correction-explicit})
contribute additional terms beyond the scalar level
at every genus $g \ge 2$.
\end{proof}

\begin{remark}[Genus~$1$ scalar coefficient and BTZ one-loop measure]
\label{rem:ent-btz-three-routes}
\index{BTZ black hole!verification routes}
The algebraic genus-$1$ scalar coefficient is
$F_1=\kappa/24=c/48$.  Three checks keep it separate from the BTZ
logarithmic determinant:
\begin{enumerate}[label=(\alph*)]
\item \emph{Uniform-weight scalar lane.}
 $F_1 = \kappa\cdot\lambda_1^{\mathrm{FP}}
 = (c/2)(1/24)=c/48$.
\item \emph{Determinant separation.}
 The same coefficient appears in the scalar closed-sector genus
 expansion; it does not determine the Gaussian determinant
 $-\tfrac32\log S_{\mathrm{BH}}$.
\item \emph{Selberg zeta.}
 After the Brown--Henneaux gravitational measure is supplied, the
 Selberg zeta function for the BTZ quotient
 $\Gamma \backslash \mathbb{H}^3$ is a compatibility check on the
 one-loop normalization
 \cite{Patterson-Perry01}.
\end{enumerate}
The equality $F_1=c/48$ is a genus-one algebraic identity.  The
coefficient $-3/2$ in~\eqref{eq:ent-btz-log} is a separate
one-loop determinant statement.
\end{remark}

\begin{proposition}[BTZ complementarity; \ClaimStatusConditional]
\label{prop:ent-btz-complementarity}
\index{BTZ black hole!complementarity}
For the Koszul pair
$(\mathrm{Vir}_c, \mathrm{Vir}_{26-c})$, the BTZ
entropy satisfies the following scalar complementarity identity,
whenever the effective weights are positive for both central charges:
\begin{equation}\label{eq:ent-btz-complementarity}
S_{\mathrm{BH}}(\mathrm{Vir}_c;\, h)
+ S_{\mathrm{BH}}(\mathrm{Vir}_{26-c};\, h)
\;=\;
2\pi\Bigl(
 \sqrt{\tfrac{c\,(h - c/24)}{6}}
 + \sqrt{\tfrac{(26-c)\,(h - (26-c)/24)}{6}}
\Bigr).
\end{equation}
In the semiclassical regime $h \gg c/24$, this simplifies to
$2\pi\sqrt{h/6}\,(\sqrt{c} + \sqrt{26-c})$,
with maximum at $c = 13$ \textup{(}self-dual point\textup{)},
where $\sqrt{c} + \sqrt{26-c} = 2\sqrt{13}$.
The one-loop free energy sum
$F_1(\mathrm{Vir}_c) + F_1(\mathrm{Vir}_{26-c})
= 13/24$
is the genus-$1$ shadow of the complementarity constant
$K = 13$.
\end{proposition}

\begin{proof}
By additivity of $\kappa$:
$F_1(c) + F_1(26-c) = c/48 + (26-c)/48 = 26/48 = 13/24$.
Substituting $c$ and $26-c$ into~\eqref{eq:ent-btz-leading} gives
the displayed entropy sum.
The maximum of $f(c) = \sqrt{c} + \sqrt{26-c}$ is at
$f'(c) = 0$, giving $c = 13$, where
$f(13) = 2\sqrt{13}$ (concavity of $\sqrt{\cdot}$).
\end{proof}

\begin{remark}[Monster module]
\label{rem:ent-btz-monster}
\index{Monster module!BTZ entropy}
For the Monster module $V^\natural$ at $c = 24$:
$\kappa = 12$, $F_1 = 1/2$,
$S_{\mathrm{BH}} = 4\pi\sqrt{h-1}$ at leading order
\textup{(}here $h_{\mathrm{eff}} = h - c/24 = h - 1$\textup{)}.
The McKay--Thompson series
$J(\tau) = q^{-1} + 196884q + \cdots$ gives the graded dimensions of
the boundary module.  In an extremal-AdS$_3$ interpretation these
graded dimensions supply candidate BTZ degeneracies; the Monster acts
on $V^\natural$, and its action becomes a black-hole state symmetry
only after the gravitational dual has been specified.
\end{remark}

\begin{remark}[BPS entropy from the shadow tower]
\label{rem:bps-entropy-shadow}
\index{BPS black hole!entropy from shadow tower|textbf}
\index{Strominger--Vafa formula!shadow derivation}
For the Virasoro boundary theory $\mathrm{Vir}_c$ with
$c = 2\kappa$, the Cardy formula for a BPS sector of level
$n$ \textup{(}semiclassical weight $h_{\mathrm{eff}} = n$\textup{)}
reduces to
\begin{equation}\label{eq:bps-entropy-shadow}
S_{\mathrm{BH}}
\;=\;
2\pi\sqrt{\frac{\kappa\,n}{3}},
\end{equation}
which rewrites the Cardy/Strominger--Vafa coefficient
\cite{Strominger-Vafa96} in the Virasoro shadow normalization
$c=2\kappa$.  Sanity checks: at $\kappa = 1$, $n = 3$,
$S_{\mathrm{BH}} = 2\pi$; at $\kappa = 13/2$
\textup{(}the Koszul self-dual point $c = 13$\textup{)},
$n = 3$, $S_{\mathrm{BH}} = 2\pi\sqrt{13/2} \approx 16.0$.
If the linear Page-curve model of
Conjecture~\ref{conj:ent-page-curve} applies, the crossing time is
\begin{equation}\label{eq:bps-page-time}
t_P \;=\; \frac{3\,S_{\mathrm{BH}}}{13},
\end{equation}
which is $c$-independent: only the Koszul conductor
$K = 13$ of the Virasoro Koszul pair
$(\mathrm{Vir}_c, \mathrm{Vir}_{26-c})$ enters the two-line scalar
model, not the individual central charge. Higher-genus contributions
follow the multi-weight genus expansion
$F_g = \kappa\,\lambda_g^{\mathrm{FP}} + \delta F_g^{\mathrm{cross}}$
\textup{(}Theorem~\ref{thm:multi-weight-genus-expansion},
\textsc{all-weight}: the scalar formula holds without
cross-channel correction at uniform weight and at $g = 1$;
cross-channel corrections
$\delta F_g^{\mathrm{cross}}$ are required for $g \ge 2$
at multi-weight\textup{)}. Under the gravitational-dual hypothesis
of Conjecture~\ref{conj:ent-qes}, complementarity
\textup{(}Theorem~\ref{thm:quantum-complementarity-main}\textup{)}
supplies the shadow connection Ward identity whose physical image is
expected to match QES stationarity: the algebraic condition is the
vanishing of the shadow one-form $\iota_\xi(r^{\mathrm{sh}})$ on the
complementary Lagrangian
\cite{Hartle-Hawking83}. See
Proposition~\ref{prop:ent-btz-complementarity} for the
pair $(\mathrm{Vir}_c,\mathrm{Vir}_{26-c})$ instantiation.
\end{remark}

\begin{computation}[The $-3/2$ logarithmic coefficient; determinant
derivation and shadow non-derivation]
\label{comp:bps-log-three-ways}
\index{BPS black hole!logarithmic correction}
The subleading structure $S = S_0 - \tfrac{3}{2}\log S_0 + O(1)$
in equation~\eqref{eq:ent-btz-log}, with $S_0 = S_{\mathrm{BH}}$,
has one standard BTZ/Cardy determinant derivation and one algebraic
shadow compatibility check:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Cardy one-loop at large $n$.}
 Gaussian fluctuation around the saddle $\tau_* = i\sqrt{c/(24n)}$
 produces a determinant $(\det K)^{-1/2}$ with three soft modes
 \textup{(}two translations plus dilation\textup{)}, yielding
 $-\tfrac{3}{2}\log S_0$ \cite{Carlip98,Cardy86}.
\item \emph{Shadow tower compatibility.}
 The quartic shadow projection $Q^{\mathrm{contact}}$ for
 $\mathrm{Vir}_c$ gives
 $S_4(\mathrm{Vir}_c) = 10/[c(5c+22)]$.  This non-zero
 contact datum supplies the degree-$4$ term in the shadow-side
 saddle expansion.  It cannot by itself determine the universal
 coefficient $-\tfrac32$: the function
 $10/[c(5c+22)]$ varies with~$c$, whereas the stated BTZ determinant
 coefficient is independent of~$c$ for the fixed ensemble.  After the
 Cardy normalization of the quadratic fluctuation determinant is
 imposed, the shadow-side Hessian package is compatible with the
 coefficient.
\item \emph{Hartle--Hawking inner product.}
 A direct evaluation of
$\langle\Psi_{\mathrm{HH}}|\Psi_{\mathrm{HH}}\rangle$ with the
shadow connection as a bulk flat connection requires a physical
 state, measure, and gauge fixing compatible with the chosen
 gravitational dual \cite{Hartle-Hawking83}.  Those data are not
 supplied by the shadow obstruction tower.
\end{enumerate}
The Cardy/BTZ route derives the saddle coefficient $-\tfrac32$.
The shadow route proves compatibility and the non-derivation statement:
quartic shadow data alone do not imply the logarithmic determinant.
\end{computation}

% ======================================================================
%
% 7. PAGE CURVE FROM KOSZUL COMPLEMENTARITY
%
% ======================================================================

\section{The Page curve from Koszul complementarity}
\label{sec:ent-page-curve}
\index{Page curve!from Koszul complementarity|textbf}
\index{island formula!Koszul interpretation}

\begin{conjecture}[Page curve from complementarity; \ClaimStatusConjectured]
\label{conj:ent-page-curve}
\index{Page curve|textbf}
\textbf{Type signature.}  Quadrant: open with conjectural gravitational
dual.  Presentation: scalar two-line model on the Virasoro Koszul
pair $(\mathrm{Vir}_c,\mathrm{Vir}_{26-c})$.  Level: $5$.  Hypothesis
package: Setup~\ref{setup:ent-framework} (EH1)--(EH3); existence of
the Verdier dual $\cA^!=D_{\Ran}(\cA^{\mathrm i})$ as a chiral algebra
controlling the island saddle; gravitational-dual identification of
the linear growth rates with Hawking radiation emission and island
absorption.

\emph{Scope.} The mathematical content of this conjecture is the
elementary crossing-time computation given the two linear
growth rates below. The physical identification of $c/6$ and
$(26-c)/6$ with Hawking radiation emission and island absorption
respectively, and the identification of the crossing with the
Page transition, are heuristic:
they require a gravitational dual in which the Verdier-dual sector
$\cA^!=D_{\Ran}(\cA^{\mathrm i})$, or its bar complex when this sector
carries the needed chiral algebra structure, controls the island
saddle. This identification is extra physical input.

\smallskip
Let $(\mathrm{Vir}_c, \mathrm{Vir}_{26-c})$ be the Virasoro
Koszul pair with entanglement growth rates
$v = c/6$ \textup{(}matter\textup{)} and
$v' = (26-c)/6$ \textup{(}Koszul dual\textup{)}.
The Page curve of the radiation entropy is:
\begin{equation}\label{eq:ent-page-curve}
S_{\mathrm{rad}}(t)
\;=\;
\min\!\bigl(
 S_{\mathrm{Hawking}}(t),\;
 S_{\mathrm{island}}(t)
\bigr),
\end{equation}
where:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Hawking phase} ($t < t_P$):
 $S_{\mathrm{Hawking}}(t) = (c/6)\,t$.

\item \emph{Island phase} ($t > t_P$):
 $S_{\mathrm{island}}(t)
 = S_{\mathrm{BH}} - ((26-c)/6)\,t$.

\item \emph{Page time}:
 \begin{equation}\label{eq:ent-page-time}
 t_P \;=\; \frac{3\,S_{\mathrm{BH}}}{13}
 \;=\;
 \frac{6\,S_{\mathrm{BH}}}{c + (26-c)}.
 \end{equation}
 The denominator is the complementarity constant
 $c + c' = 26$, equivalently $\kappa + \kappa' = 13$
 \textup{(}Theorem~\textup{\ref{thm:entanglement-complementarity}}\textup{)}.
\end{enumerate}
\end{conjecture}

\begin{remark}[Crossing computation]
The Hawking phase growth rate $c/6$ is the Calabrese--Cardy
entanglement production rate after a local quench, under the
gravitational-dual identification with Hawking radiation emission.
The island phase uses the Verdier-dual Virasoro rate $(26-c)/6$:
once the dual sector $\mathrm{Vir}_{26-c}$ controls the saddle, the
entropy is governed by $\kappa'=(26-c)/2$.

The Page time is determined by the crossing condition:
the two branches
$S_{\mathrm{Hawking}}(t) = (c/6)t$ (increasing)
and
$S_{\mathrm{island}}(t) = S_{\mathrm{BH}} - ((26{-}c)/6)t$
(decreasing) intersect when
\[
\frac{c}{6}\,t_P = S_{\mathrm{BH}} - \frac{26{-}c}{6}\,t_P,
\qquad
t_P\,\frac{c + (26{-}c)}{6} = S_{\mathrm{BH}},
\qquad
t_P = \frac{6\,S_{\mathrm{BH}}}{26}
= \frac{3\,S_{\mathrm{BH}}}{13}.
\]
\end{remark}

\begin{corollary}[Self-dual two-line Page model;
\ClaimStatusConditional]
\label{cor:ent-page-self-dual}
\index{Page curve!self-dual point}
In the scalar two-line model of
Conjecture~\textup{\ref{conj:ent-page-curve}}, at the self-dual point
$c = 13$:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The Hawking and island growth rates are equal:
 $v = v' = 13/6$.
\item The Page time is $t_P = 3S_{\mathrm{BH}}/13$
 and the Page curve is symmetric about~$t_P$.
\item The Page entropy is
 $S_{\mathrm{Page}} = S_{\mathrm{BH}}/2$,
 reflecting the Virasoro involution $c\leftrightarrow 26-c$ at its
 fixed point.
\end{enumerate}
\end{corollary}

\begin{proof}
At $c = 13$: $\kappa = \kappa' = 13/2$, so $v = v' = 13/6$.
The crossing condition gives
$t_P = 6S_{\mathrm{BH}}/26 = 3S_{\mathrm{BH}}/13$.
The Page entropy $S_{\mathrm{Page}}
= (13/6)\cdot 3S_{\mathrm{BH}}/13 = S_{\mathrm{BH}}/2$.
\end{proof}

\begin{remark}[Island formula as Koszul dual dominance]
\label{rem:ent-island-koszul}
\index{island formula!Koszul interpretation}
In the language of
Penington~\cite{Penington19} and
Almheiri--Engelhardt--Marolf--Maxfield~\cite{AEMM19},
the modular-Koszul dictionary assigns the \emph{island} saddle to
the Verdier-dual sector
$\cA^!=D_{\Ran}(\cA^i)$, when that sector is represented by a chiral
algebra with its own replica datum.  The transition from the Hawking
phase to the island phase is then modelled by the exchange of dominant
saddle
in the complementarity sum
$\mathbf{C}_g(\cA) = \mathbf{Q}_g(\cA) \oplus
\mathbf{Q}_g(\cA^!)$
(Theorem~\ref{thm:quantum-complementarity-main}).
Under that dictionary, the two scalar branches are controlled by
$\kappa(\cA)$ at early times and by $\kappa(\cA^!)$ at late times;
the complementarity constant $\kappa + \kappa' = 13$
determines the crossover.
\end{remark}

\begin{remark}[Page curve from Koszul complementarity; \ClaimStatusHeuristic]
\label{rem:page-curve-complementarity}
\index{Page curve!from complementarity constant}
The two-line Page model is the Virasoro complementarity sum
$\kappa(\mathrm{Vir}_c) + \kappa(\mathrm{Vir}_{26-c}) = 13$
(Theorem~\ref{thm:quantum-complementarity-main}).
The Hawking channel grows entropy at rate $c/6$;
the island channel decreases it at rate $(26-c)/6$.
The crossing condition gives a $c$-independent Page time
\[
 t_P = \frac{3 S_{\mathrm{BH}}}{13},
\]
because the $c$ cancels algebraically from
$\kappa + \kappa' = 13$.
At the Koszul self-dual point $c = 13$:
$S_{\mathrm{Page}} = S_{\mathrm{BH}}/2$
for the two linear scalar branches.  Self-duality kills the
duality-odd part of any correction written as a function of
$\delta_\kappa=\kappa-\kappa'=c-13$; it does not kill the
duality-even shadow tower.  Indeed
$S_4(\mathrm{Vir}_{13})=10/(13\cdot87)\neq0$ and
$\Delta(13)=40/87$, so the class-$\mathsf M$ tower remains
non-trivial at the fixed point.

\emph{Scope}: the scalar-level complementarity and
the Page time formula use only
Theorems~\ref{thm:quantum-complementarity-main}
and~\ref{thm:ent-scalar-entropy} (proved).
The identification of the shadow coefficients with FLM bulk
entropy corrections, and the identification of the crossing with
the physical Page transition, require a gravitational dual and are
heuristic.
\end{remark}

% ======================================================================
%
% 8. DE SITTER ENTROPY FROM ANALYTIC CONTINUATION
%
% ======================================================================

\section{de~Sitter entropy from analytic continuation of the shadow obstruction tower}
\label{sec:ent-desitter}
\index{de Sitter entropy!from shadow tower|textbf}
\index{analytic continuation!shadow tower}

\begin{conjecture}[de~Sitter shadow obstruction tower; \ClaimStatusConjectured]
\label{conj:ent-desitter}
\index{de Sitter entropy|textbf}
After the analytic continuation $\ell\mapsto i\ell$ from
$\mathrm{AdS}_3$ to $\mathrm{dS}_3$, choose the real de~Sitter
section in which
$c_{\mathrm{dS}} = 3\ell_{\mathrm{dS}}/(2G)$ and
$\kappa_{\mathrm{dS}} = c_{\mathrm{dS}}/2$.
The shadow obstruction tower continues as:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Gibbons--Hawking entropy.}
 The tree-level entropy of the cosmological horizon is
 \begin{equation}\label{eq:ent-ds-leading}
 S_{\mathrm{dS}}
 \;=\;
 \frac{\pi\,c_{\mathrm{dS}}}{3}
 \;=\;
 \frac{\pi\ell_{\mathrm{dS}}}{2G},
 \end{equation}
 which is the area of the cosmological horizon
 in $2{+}1$ dimensions.

\item \emph{One-loop correction.}
 The genus-$1$ free energy continues to
 $F_1 = \kappa_{\mathrm{dS}}/24 = c_{\mathrm{dS}}/48$,
 contributing a real quantum correction to the
 Gibbons--Hawking entropy.

\item \emph{Nariai limit.}
 The analytic continuation of the self-dual point
 $c = 13$ gives $c_{\mathrm{dS}} = 13$
 (the Nariai solution, where the cosmological and
 black hole horizons coincide). At this point
 $\kappa_{\mathrm{dS}} = 13/2$ and the
 complementarity is symmetric.

\item \emph{Hilbert space dimension.}
 The Banks conjecture
 $\dim(\mathcal{H}_{\mathrm{dS}})
 = \exp(S_{\mathrm{dS}})
 = \exp(\pi c_{\mathrm{dS}}/3)$
 is consistent with the convergent shadow obstruction tower
 \textup{(}Bernoulli decay\textup{)}.
\end{enumerate}
\end{conjecture}

\begin{remark}[Analytic-continuation input]
Under $\ell \mapsto i\ell$, the Brown--Henneaux formula
$c = 3\ell/(2G)$ maps to an imaginary central charge.
In Convention~B (real section), one takes
$\kappa_{\mathrm{dS}} = c_{\mathrm{dS}}/2$ as a real
parameter directly, yielding real free energies.
The Gibbons--Hawking entropy then follows from the genus-$0$
shadow projection, and the genus expansion provides quantum
corrections. The identification of~\eqref{eq:ent-ds-leading}
with the cosmological horizon area is the dS/CFT
correspondence (Strominger~\cite{Strominger01}).
\end{remark}

% ======================================================================
%
% 9. JT GRAVITY AS SCHWARZIAN LIMIT OF THE SHADOW TOWER
%
% ======================================================================

\section{JT gravity as Schwarzian limit of the shadow obstruction tower}
\label{sec:ent-jt}
\index{JT gravity!from shadow tower|textbf}
\index{Weil--Petersson volumes!shadow tower}

\begin{conjecture}[JT gravity from the shadow obstruction tower;
\ClaimStatusConjectured]
\label{conj:ent-jt-shadow}
\index{JT gravity|textbf}
In the Schwarzian limit $c \to \infty$ with
$\ell = 2Gc/3$ held fixed, the Virasoro shadow obstruction tower
degenerates to the JT gravity genus expansion:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Spectral curve.}
 The shadow metric $Q_{\mathrm{Vir}}(t)$, after rescaling
 $t \mapsto t/\sqrt{c}$, limits to a trigonometric spectral
 curve whose topological recursion reproduces the JT amplitudes.
 The JT spectral curve $y = \sin(2\pi\sqrt{x})/(4\pi)$
 governs the matrix integral of Saad--Shenker--Stanford~\cite{SSS19}.

\item \emph{Genus expansion.}
 The JT partition function is
 \begin{equation}\label{eq:ent-jt-genus}
 Z_{\mathrm{JT}}(\beta)
 \;=\;
 \sum_{g \ge 0}
 e^{S_0(2-2g)}\,Z_g(\beta),
 \end{equation}
 where $Z_g(\beta)$ is expressed in terms of
 Weil--Petersson volumes $V_{g,1}(b)$ via the Laplace
 transform. The initial data
 $V_{1,1}(b) = (b^2 + 4\pi^2)/48$
 matches the genus-$1$ shadow amplitude $F_1 = \kappa/24$
 after integration against the JT measure.

\item \emph{Shadow CohFT reconstruction.}
The shadow CohFT extracts Faber--Pandharipande
intersection numbers $\lambda_g^{\mathrm{FP}}$ that
govern the scalar contribution to the JT genus expansion.
At genus~$g$, the scalar shadow free energy
\[
F_g^{\mathrm{sc}}
=\kappa\cdot\lambda_g^{\mathrm{FP}}
\]
on the uniform-weight scalar lane, with
 $\lambda_g^{\mathrm{FP}}
 = (2^{2g-1}-1)|B_{2g}|/(2^{2g-1}(2g)!)$
 matches the leading-order JT amplitude
 in the limit $S_0 \to \infty$.
\end{enumerate}
\end{conjecture}

\begin{remark}[Schwarzian-limit evidence]
The Schwarzian limit of the Virasoro OPE produces the
Schwarzian mode~$\{f, z\}$ as the surviving degree of
freedom. The shadow connection
$\nabla^{\mathrm{sh}} = d - Q'/(2Q)\,dt$
degenerates to a trigonometric connection whose flat
sections are related to the Bessel function kernel of the
JT matrix integral. The genus-$1$ matching:
$V_{1,1}(0) = \pi^2/12$ and
$F_1 = \kappa/24 = c/48$; in the Schwarzian limit,
the Laplace transform of $V_{1,1}(b)$ gives
$Z_1(\beta) = (c/48)\beta^{-1}$, consistent with the
shadow obstruction tower at genus~$1$. The higher-genus matching
requires the full topological recursion, which agrees with
the shadow CohFT reconstruction
(Corollary~\ref{cor:topological-recursion-mc-shadow})
at the level of tautological intersection numbers.
\end{remark}

\begin{remark}[Matrix model from the shadow obstruction tower]
\label{rem:ent-jt-matrix-model}
\index{JT gravity!matrix model}
The JT spectral density
$\rho(E) = \sinh(2\pi\sqrt{E})/(4\pi^2)$ is obtained from the
shadow obstruction tower in the $c \to \infty$ limit as the
density of states in the Schwarzian quantum mechanics.
The shadow partition function
$Z^{\mathrm{sh}} = \exp(\sum F_g\,\hbar^{2g})$
converges absolutely (Bernoulli decay
$\lambda_g^{\mathrm{FP}} \sim (2\pi)^{-2g}$),
in contrast to the JT perturbative expansion which
diverges as $(2g)!$ and requires
non-perturbative completions
via the matrix integral \cite{SSS19}.
\end{remark}

\section{Entanglement and Koszul conductor on the B-family}
\label{sec:ent-supplement}

\begin{remark}[Entanglement $c/3 \log$-law and K3 Mukai doubling]
\label{rem:ent-cthird-K3}
At the K3 chiral algebra $\mathcal{H}_{\mathrm{Muk}}$ with
$c=24$, the scalar entropy coefficient is
\[
S_{EE}=8\log(L/\varepsilon).
\]
The same integer occurs in the B-family Koszul conductor
\[
K^{\kappa_{\mathrm{ch}}}
(\mathcal{H}_{\mathrm{Muk}}(K3))
=2\,c_+(\mathrm{Mukai}(K3))=8.
\]
It has three independent realizations: Mukai doubling
$2c_+=8$, the monodromy order of $\mathcal L^{\Delta_5}$ around the
Humbert divisor $H_1\subset\overline{\mathcal A_2}$, and the Lusztig
specialisation $\ell=8$ at $\zeta^8=1$, $\hbar^2=-1/8$.  On the
$\mathcal B$-family this gives
$\hbar^2 K^{\kappa_{\mathrm{ch}}}=-1$.
The equality of the two displayed integers compares two normalized
invariants: the central-charge coefficient $c/3$ on the replica line
and the B-family conductor.  It is not a rule replacing the
Calabrese--Cardy central charge by $\kappa$.
\end{remark}

\section{Formal anomaly coefficient for negative effective
\texorpdfstring{$c$}{c}}
\label{sec:ent-supplement-ii}

\begin{remark}[Negative formal coefficient at $c_{\mathrm{eff}} = -166$;
\ClaimStatusProvedHere]
\label{rem:ent-negative}
\index{entanglement entropy!negative coefficient!anomaly}
\index{c effective@$c_{\mathrm{eff}} = -166$!entanglement reading}
\index{topological entanglement!anomaly signature}
At the K3 BKM chiral bialgebra $\mathbf H_{\Delta_5}$ with formal
chiral central charge $c_{2d} = -214$ and effective central charge
$c_{\mathrm{eff}} = -166 = -2\cdot 83$ (Vol~I
Remark~\ref{rem:stqp-ceff-unitarity}), the formal
Calabrese--Cardy coefficient obtained by inserting
$c_{\mathrm{eff}}$ into $(c/3)\log(L/\varepsilon)$ is
\[
S_{\mathrm{EE}}^{\mathrm{eff}}(\mathbf H_{\Delta_5})
\;=\;
\frac{c_{\mathrm{eff}}}{3}\,\log(L/\varepsilon)
\;=\;
-\frac{166}{3}\,\log(L/\varepsilon).
\]
The coefficient is negative. Entanglement entropy of a Hilbert-space
density matrix is non-negative by definition,
$S = -\mathrm{tr}\rho_A\log\rho_A\ge 0$.  Thus this number is a formal
anomaly coefficient rather than an entropy.  The correct reading is that
$\mathbf H_{\Delta_5}$ is \emph{not a unitary CFT at the
whole-module level} (Vol~I
Remark~\ref{rem:stqp-ceff-unitarity};
Corollary~\ref{cor:stqp-real-imag-dichotomy}); the
negative $c_{\mathrm{eff}}$ quantifies the gravitational /
topological anomaly obstructing a unitary CFT description, not
an entanglement entropy of a Hilbert space.
\end{remark}

\begin{proposition}[Real-root unitary submodule entanglement;
\ClaimStatusProvedHere]
\label{prop:ent-real-root}
\index{entanglement entropy!real-root submodule}
On the real-root unitary submodule
$V^{\mathrm{unit}}\subset\mathbf H_{\Delta_5}$
(Vol~I Proposition~\ref{prop:stqp-unitary-spectrum};
positive-definite $2$-plane $P\subset\mathfrak h_{\mathbb R}$ of
Vol~I Proposition~\ref{prop:stqp-signature}), the
Calabrese--Cardy entanglement formula applies with the genuine
positive-definite central charge
\[
c_{\mathrm{unit}}(V^{\mathrm{unit}})
\;=\;
\mathrm{rk}(P)
\;=\;
2,
\]
giving
\[
S_{\mathrm{EE}}(V^{\mathrm{unit}})
\;=\;
\frac{2}{3}\,\log(L/\varepsilon)
\;>\;0,
\]
a positive, physical, bosonic entanglement entropy of a rank-$2$
free-boson vertex algebra $\mathrm{Fock}(P)$ on the positive-definite
$2$-plane. The remaining $c_{\mathrm{eff}}/24 - 2/24 = -168/24 = -7$
of the ``effective'' central charge budget lives on the
imaginary-root sector (hyperbolic direction $L$) and does not
contribute to the unitary entanglement; it tracks the gravitational
anomaly.
\end{proposition}

\begin{proof}
The real-root unitary submodule is a Frenkel--Kac vertex algebra
on the positive-definite rank-$2$ lattice $P^* \cap
\Lambda_{\mathrm{BKM}}$, whose central charge equals the rank of
the lattice (Frenkel--Lepowsky--Meurman 1988 \S 8.8; Kac 1998
\emph{Vertex Algebras for Beginners} Proposition~3.6):
$c = \mathrm{rk}(P) = 2$. The Calabrese--Cardy formula
$S_{\mathrm{EE}} = (c/3)\log(L/\varepsilon)$ applies to every
unitary $2$d CFT with positive central charge
(Calabrese--Cardy 2004 eq.~(3.8); derivation via twist-operator
dimension $h_n = (c/24)(n - 1/n)$) and gives $2/3\cdot\log(L/\varepsilon)$.
Independence from the anomaly reading: the full-module
$c_{\mathrm{eff}} = -166$ formal coefficient of
Remark~\ref{rem:ent-negative} is the partition-function
shift, not a bona fide entanglement entropy; the genuine positive
entanglement comes only from the unitary submodule with central
charge $+2$.
\end{proof}

\begin{remark}[Topological anomaly reading of $c_{\mathrm{eff}} < 0$;
\ClaimStatusHeuristic]
\label{rem:ent-topological-anomaly}
\index{topological anomaly!c effective negative}
\index{Manschot--Moore!anti-holomorphic counting}
The negative sign of $c_{\mathrm{eff}} = -166$ matches the
anti-holomorphic Cardy counting of
Manschot--Moore 2007 arXiv:0712.0573 \S 3 and
Dijkgraaf--Verlinde--Verlinde 1997 \S 6 on K3 BPS counting: BKM
BPS states are counted against an anti-holomorphic background,
and the entanglement reading $(c_{\mathrm{eff}}/3)\log(L/\varepsilon)$
is used here only as the \emph{gravitational anomaly coefficient} of
the holographic dual, rather than as a conventional Calabrese--Cardy
entanglement on a unitary Hilbert space. The
$c_{\mathrm{eff}}/24 = -83/12$ weight appears in the Borcherds
denominator identity expansion as the leading polar term at the
maximal-rank cusp of $\mathcal A_2$, tracking the gravitational
anomaly of the 3d dual (anti-de Sitter gravity with
Chern--Simons level proportional to $c_{\mathrm{eff}}$; Witten
2007 arXiv:0706.3359 \S 2; cf.\ Vol~II Chapter~13 on the level-$3$
$\mathsf{SC}^{\mathrm{ch,top}}$-brace bulk realisation
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ as 3d quantum gravity datum). In
this
reading, the negative coefficient is a \emph{topological anomaly
signature}: a measure of how far $\mathbf H_{\Delta_5}$
is from being a unitary CFT, with the positive-definite
real-root submodule $V^{\mathrm{unit}}$ of
Proposition~\ref{prop:ent-real-root} realising the
genuine entanglement content.
\end{remark}

\begin{remark}[Koszul-locus scope and Humbert divisor degeneration]
\label{rem:ent-koszul-locus}
All three statements (the negative
$c_{\mathrm{eff}}$ anomaly reading, the real-root unitary entanglement,
the topological-anomaly interpretation) hold on the
Koszul locus
$\overline{\mathcal A_2}\setminus(H_1\cup H_4)$, where the
Gritsenko--Nikulin paramodular lift of $\Delta_5$ has maximal rank
and the Kawazumi--Zhang current $\kappa_{\mathrm{KZ}}$ is
non-degenerate. On the Humbert divisors $H_1$ and $H_4$, the
hyperbolic Cartan of Vol~I
Proposition~\ref{prop:stqp-signature} suffers a
rank-collapse (the principal minor $m_2 = 0$ becomes a full
$2$-plane degeneracy rather than an isolated isotropic
direction), unitarity on the real-root sector breaks down, and
the entanglement reading of
Proposition~\ref{prop:ent-real-root} requires
replacement before it can be physical.  A logarithmic-CFT entropy
with
$c_{\mathrm{log}}\log^2(L/\varepsilon)$ corrections
(Bianchi--Piazza 2012; Saleur 2013 lectures) is the expected
replacement; no such formula is asserted here for the degenerate
Humbert locus.  The Koszul-locus restriction is therefore
constitutive, not a convenience.
\end{remark}

\section{Topological entanglement and ground-state degeneracy from the 3d TQFT}
\label{sec:ent-3d-tqft}

The scalar entanglement formula
$S_{\EE} = (c/3)\log(L/\varepsilon)$ of
Theorem~\ref{thm:ent-scalar-entropy} tracks the $1+1$d boundary CFT
Calabrese--Cardy coefficient.  A different invariant appears after
one equips the K3 boundary theory with the Vol~III ribbon-category
package: at each finite PBW stage the Kerler--Lyubashenko category
defines a De~Renzi--Gainutdinov--Geer--Patureau-Mirand--Runkel
3d TQFT, and its disc topological entropy is
$\gamma_N=\log\mathcal D_N$.  This is a TQFT invariant.  It becomes
a correction to the boundary interval entropy only after a
bulk--boundary interface has been chosen.

\begin{theorem}[Topological entanglement at finite PBW stage]
\label{thm:ent-topological-entanglement}
\ClaimStatusConditional
\textbf{Type signature.}  Quadrant: open boundary of a CY-quadrant
input under the two-stage Vol~III specialisation
$\Phi_d^{(\Sigma_{d-1},C)}=\Sp^{\mathrm{ch}}_{\Sigma_{d-1},C}\circ
\Phi_d^{\mathrm{FA}}$ at the K3-row reference data $(\Sigma_{d-1},C)$
producing $\mathbf H_{\Delta_5}$.  Presentation: ribbon-category 3d
TQFT at finite PBW stage~$N$, with optional pro-limit completion.
Level: $4$ (boundary line/brane operators) with bulk--boundary
interface to a level-$1$/level-$5$ open boundary.  Hypothesis
package: bulk--boundary interface identifying the two interval
endpoints with disc defects; choice of unitary boundary sector with
central charge $c_{\mathrm{bdry}}$; trace-class Mittag--Leffler
completion for the pro-limit clause.

Let $\mathcal C_N =
\mathrm{Rep}^{\mathrm{fd}}(\mathfrak u_{\zeta_8}^{\le N}
(\widehat{\mathfrak m}_{\Delta_5}))$ be a finite PBW-stage
Kerler--Lyubashenko category in the pro-system of
Vol~III Chapter~\ref{V3-ch:modular-trace}
Theorem~\ref{V3-thm:modtr-Plancherel-KerlerLyubashenko} at the
specialisation data $(\Sigma_{d-1},C)$, and let
$Z_N^{\mathrm{DGGPR}}$ be the corresponding DGGPR 3d TQFT.  Define
\[
 \mathcal D_N(\mathbf H_{\Delta_5})
 \;=\;
 \sqrt{\sum_{\lambda\in\Lambda^{\le N}}d_\lambda^2},
 \qquad
 d_\lambda
 \;:=\;
 \dim_{\mathrm{qu}}(P_\lambda),
\]
where the finite sum runs over indecomposable projective covers at
stage~$N$ and $d_\lambda$ is the Kerler--Lyubashenko quantum
dimension.  The topological entanglement entropy of a disc-like
spatial region in $Z_N^{\mathrm{DGGPR}}$ is
\[
 \boxed{\;
 \gamma_N(\mathbf H_{\Delta_5})
 \;=\;
 \log\mathcal D_N(\mathbf H_{\Delta_5}).\;}
\]
If the Mittag--Leffler Plancherel trace has a trace-class limit on the
chosen completion, one may set
$\gamma_\infty=\lim_N\gamma_N$; without this completion no finite
number is asserted for the full pro-limit.  Under an additional
bulk--boundary coupling identifying the two interval endpoints with
disc defects of the 3d TQFT, and after choosing a unitary boundary
sector with central charge $c_{\mathrm{bdry}}$, the boundary entropy
takes the form
\[
 S_{\EE}(\Sigma)
 \;=\;
 \frac{c_{\mathrm{bdry}}}{3}\log\frac{L}{\varepsilon}
 \;-\;
 2\,\gamma_N(\mathbf H_{\Delta_5})
 \;+\;
 \mathcal O(1/L),
\]
with the coefficient $-2\gamma_N$ reflecting the two boundary
components of the entangling interval.  For the whole
$\mathbf H_{\Delta_5}$ module, $c_{\mathrm{bdry}}=c_{\mathrm{eff}}$
is only the formal anomaly coefficient of
Remark~\ref{rem:ent-negative}; for the real-root unitary sector,
$c_{\mathrm{bdry}}=2$.
\end{theorem}

\begin{proof}
For each finite stage~$N$, the DGGPR construction applies to the
finite Kerler--Lyubashenko ribbon category $\mathcal C_N$.  The
Kitaev--Preskill and Levin--Wen topological-entanglement formula gives
$\gamma_N=\log\mathcal D_N$ in the semisimple string-net case; the
Gainutdinov--Runkel non-semisimple extension replaces simples by
indecomposable projective covers and the ordinary quantum dimension by
the Kerler--Lyubashenko quantum trace.

The Calabrese--Cardy $(c_{\mathrm{bdry}}/3)\log(L/\varepsilon)$
leading term is Theorem~\ref{thm:ent-scalar-entropy} applied to the
chosen unitary boundary sector.  The topological subtraction does not
follow from the scalar chiral calculation; it is the extra TQFT
interface input.  At finite~$N$ the Hopf-algebraic
normalisation is controlled by Radford's $S^4$ formula together with
the Kerler--Lyubashenko ribbon anomaly.  Passing to the full
$\mathfrak u_{\zeta_8}=\lim_N\mathfrak u_{\zeta_8}^{\le N}$ requires
the trace-class Mittag--Leffler completion of Vol~III
Theorem~\ref{V3-thm:modtr-Plancherel-ML-limit}; the theorem therefore
states a finite-stage invariant and records the pro-limit as an
additional hypothesis.
\end{proof}

\begin{theorem}[Ground-state degeneracy on $T^2$ at finite PBW stage]
\label{thm:ent-GSD-T2}
\ClaimStatusConditional
\textbf{Type signature.}  Quadrant: open boundary of CY-quadrant data
specialised through the Vol~III two-stage functor
$\Phi_d^{(\Sigma_{d-1},C)}$ to the K3 row.  Presentation:
finite-stage Kerler--Lyubashenko categorical Hochschild $H_0$ on
$T^2$.  Level: $4$ at finite PBW stage.  Hypothesis package: finite
stage~$N$; identification of $T^2$ state space with categorical
$\mathrm{HH}_0^{\mathrm{cat}}$ via Keller's trace; trace-class
Mittag--Leffler completion for the pro-limit clause.

At finite PBW stage~$N$, the ground-state degeneracy of the
Hamiltonian 3d TQFT $Z_N^{\mathrm{DGGPR}}$ on a spatial two-torus
$T^2$ equals the dimension of the state space:
\[
 \mathrm{GSD}_N(T^2)
 \;=\;
 \dim Z_N^{\mathrm{DGGPR}}(T^2)
 \;=\;
 \dim\mathrm{HH}_0^{\mathrm{cat}}(\mathcal C_N),
\]
where $\mathrm{HH}_0^{\mathrm{cat}}$ denotes the categorical
Hochschild zero-homology of the finite tensor category
$\mathcal C_N$, distinct from chiral Hochschild
$\mathrm{ChirHoch}^\bullet$ and topological Hochschild
$\mathrm{THH}$.  On the real-root Kerler--Lyubashenko stratum,
\[
 |\Lambda^{\mathrm{re}}|
 \;=\;
 8^{|\Phi^{\mathrm{real}}_+|+\mathrm{rank}}
 \;=\;
 8^{126+3}
 \;=\;
 8^{129}.
\]
This is a projective-index cardinality, equivalently the positive
Borel real-root count; it is not the total dimension of the full
two-sided BKM small form.  For the full pro-limit, the state space is
the pro-vector space $\lim_N Z_N^{\mathrm{DGGPR}}(T^2)$, and no finite
ground-state degeneracy is claimed without a trace-class completion.
The word ``ground-state'' refers to the topological state space of the
3d TQFT; a physical Hilbert-space interpretation requires a unitary
Hamiltonian realization.
\end{theorem}

\begin{proof}
The DGGPR universal construction identifies the state space on
$\Sigma_g$ with
$\mathrm{Hom}_{\mathcal C_N}(\mathbf 1,\mathcal L_N^{\otimes g})$.
At $g=1$ this is
$\mathrm{Hom}_{\mathcal C_N}(\mathbf 1,\mathcal L_N)$, and Keller's
categorical trace identifies it with
$\mathrm{HH}_0^{\mathrm{cat}}(\mathcal C_N)$.  The Hamiltonian
interpretation of the 3d TQFT makes this vector space the
ground-state subspace on $T^2$.

The number $8^{129}$ is supplied by the sharpened Vol~III root-of-unity
calculus at the specialisation $(\Sigma_{d-1},C)$ producing the
$\Delta_5$/Igusa row: $|\Phi^{\mathrm{real}}_+|=126$ and
$\mathrm{rank}=3$, so the real-root positive-Borel/projective-index
count is $8^{126+3}$.  Vol~III's pro-limit theorem separates this
cardinality from the full small-form dimensions
$\dim\mathfrak u_{\zeta_8}^{\le N}=8^{2d(N)+3}$ and from the
pro-finite object
$\mathfrak u_{\zeta_8}=\lim_N\mathfrak u_{\zeta_8}^{\le N}$.
\end{proof}

\begin{remark}[Topological entanglement and derived-centre scope]
\label{rem:ent-topological-entanglement-derived-centre}
The topological entanglement
$\gamma_N=\log\mathcal D_N$ of
Theorem~\ref{thm:ent-topological-entanglement} is first a finite-stage
ribbon tensor-category invariant of
$\mathcal C_N=
\mathrm{Rep}^{\mathrm{fd}}(\mathfrak u_{\zeta_8}^{\le N}
(\widehat{\mathfrak m}_{\Delta_5}))$: it depends on
projective-cover quantum dimensions in the Kerler--Lyubashenko coend.
The bulk on the open Beilinson tower is the level-$3$ derived chiral
centre $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)\simeq
C^\bullet_{\mathrm{ch}}(\cA,\cA)$, not the level-$2$ bar coalgebra
$B(\cA)$; the bar object encodes the twisting datum on the
Koszul-locus reconstruction
$\Omega B(A_b)\xrightarrow{\sim} A_b$ at level~$1$, while
$\gamma_N$ becomes a chiral derived-centre invariant only after one
supplies an open/closed comparison functor
\[
 \mathfrak F_N\colon Z_{\mathrm{KL}}(\mathcal C_N)
 \longrightarrow
 Z^{\mathrm{der}}_{\mathrm{ch}}(\mathbf H_{\Delta_5})
\]
where $Z_{\mathrm{KL}}(\mathcal C_N)$ denotes the
Kerler--Lyubashenko ribbon centre/coend package of $\mathcal C_N$.
The functor must be compatible with the ribbon trace and the
Kerler--Lyubashenko coend.
Kazhdan--Lusztig at a root of unity and its logarithmic extensions
provide the expected bridge; the bridge is an additional input, not
a consequence of the Calabrese--Cardy calculation.

Theorem~C governs the chiral derived centre and its
complementarity.  Theorem~H governs the chiral Hochschild complex
$\ChirHoch^\bullet$ and its amplitude $\{0,1,2\}$.  Neither theorem
identifies the categorical Hochschild group
$\mathrm{HH}^{\mathrm{cat}}_0(\mathcal C)$, the topological
Hochschild theory of a ring spectrum, and the ribbon-category
coend trace.  Under the functor $\mathfrak F_N$, the equality
$\gamma_N(\mathbf H_{\Delta_5})=\log\mathcal D_N$ says that the
finite-stage topological entanglement coefficient is the logarithmic
volume of the bulk ribbon centre; without that bridge it remains a
three-dimensional TQFT invariant.  Passing from $\gamma_N$ to
$\gamma_\infty$ requires the trace-class Mittag--Leffler completion
named in Theorem~\ref{thm:ent-topological-entanglement}.
\end{remark}

\begin{remark}[Genus-two topological entanglement and Siegel-cusp correction]
\label{rem:ent-Sigma2-topological}
At finite PBW stage, and under the same bulk--boundary interface
hypothesis as Theorem~\ref{thm:ent-topological-entanglement}, the
genus-two correction replaces the single-interval vacuum functional by
the Vol~III genus-two DGGPR/Plancherel partition function
$\mathcal Z_{\Sigma_2}=1/\Phi_{10}^{\mathrm{un}}(Z)$ at the
specialisation data $(\Sigma_{d-1},C)$
\textup{(}Chapter~\ref{V3-ch:modular-trace},
Theorem~\ref{V3-thm:modtr-Zsigma2-Phi10}\textup{)}:
\[
 S_{\EE}^{\Sigma_2}(\Sigma)
 \;=\;
 \frac{c_{\mathrm{bdry}}}{3}\log\frac{L}{\varepsilon}
 \;-\;
 2\gamma_N(\mathbf H_{\Delta_5})
 \;+\;
 \log\Phi_{10}^{\mathrm{un}}(Z)
 \;+\;
 \mathcal O(1/L),
\]
where $\log\Phi_{10}^{\mathrm{un}}(Z) =
\log\prod_\alpha(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}$
is the BKM Weyl--Kac--Borcherds denominator evaluated at the Siegel
modulus $Z$. The positivity problem of
Remark~\ref{rem:ent-negative} (bulk $c_{\mathrm{eff}} = -166$
gives a negative leading coefficient) is not resolved by the genus-two
correction: the unitary sector is still the real-root submodule
$V^{\mathrm{unit}}$ with $c_{\mathrm{unit}} = 2$ of
Proposition~\ref{prop:ent-real-root}, and the topological
correction $\gamma_N$ on the unitary sector adds
$\log\mathcal D_N(\mathfrak h_{\mathrm{real}})$ to the standard free-boson
entanglement. The genus-two extension to the full $\mathbf H_{\Delta_5}$
module inherits the anomaly signature rather than curing it.
\end{remark}

\begin{proposition}[Knill--Laflamme scope for finite-stage
topological entanglement; \ClaimStatusProvedHere]
\label{prop:ent-kl-scope}
\index{Knill--Laflamme condition!topological entanglement scope}
The finite-stage data
\[
 \bigl(\mathcal C_N,\; \gamma_N=\log\mathcal D_N,\;
 Z_N^{\mathrm{DGGPR}}(T^2)\bigr)
\]
do not by themselves define a Knill--Laflamme quantum
error-correcting code.  They define a ribbon-category TQFT invariant
and a topological state space.  A Knill--Laflamme code additionally
requires:
\begin{enumerate}[label=\textup{(\roman*)}]
\item a physical Hilbert space $\mathcal H_{\mathrm{phys}}$ with a
 positive Hermitian inner product;
\item a code projector $P_{\mathcal C}$;
\item an error algebra $\mathcal E$ acting on
 $\mathcal H_{\mathrm{phys}}$;
\item the compression identities
 \[
  P_{\mathcal C} E_i^\dagger E_j P_{\mathcal C}
  =\lambda_{ij}P_{\mathcal C}.
 \]
\end{enumerate}
The Verdier isotropic condition is only an algebraic prerequisite.
It becomes a Hilbert-space Knill--Laflamme statement only after the
physical inner product and error algebra have been supplied, as in the holographic-code
framework of Almheiri--Dong--Harlow~\cite{Almheiri-Dong-Harlow15}
and Pastawski--Yoshida--Harlow--Preskill
\cite{Pastawski-Yoshida-Harlow-Preskill15}.  On a one-dimensional
scalar conformal-block line the compression equation is automatic;
this one-channel fact does not identify the full finite-stage
$T^2$ state space with a one-dimensional code.  For genus $g\ge2$,
the physical Knill--Laflamme upgrade remains a conjectural
open/closed comparison problem.
\end{proposition}

\begin{proof}
The objects $\mathcal C_N$, $\gamma_N$, and
$Z_N^{\mathrm{DGGPR}}(T^2)$ belong to the finite ribbon-category
TQFT.  The Knill--Laflamme equation is an
identity in a Hilbert space with an adjoint operation
$E\mapsto E^\dagger$ and a chosen projector.  These data are absent
from $\gamma_N=\log\mathcal D_N$ and from the categorical trace
$\mathrm{HH}^{\mathrm{cat}}_0(\mathcal C_N)$ alone.
Even when the Verdier-isotropic summands are present, they are
algebraic data; they do not supply the physical Hilbert-space
Knill--Laflamme equation.  For a
one-dimensional code line,
$P_{\mathcal C}E_i^\dagger E_jP_{\mathcal C}$ is a scalar multiple of
$P_{\mathcal C}$, giving the automatic scalar case and no statement
about higher-dimensional state spaces.
\end{proof}

\begin{remark}[Chain-level obligations for the 3d TQFT entanglement]
\label{rem:ent-open}
Three chain-level obligations remain.
(i) \emph{Explicit PBW count}: the real-root cardinality
$|\Lambda^{\mathrm{re}}|=8^{129}$ does not enumerate the full
pro-limit; exact PBW enumeration requires the full
Shapovalov Gram matrix of
$\mathfrak u_{\zeta_8}(\widehat{\mathfrak m}_{\Delta_5})$ (Shapovalov 1972
\emph{Funct.~Anal.~Appl.}~6), known only through the rank-3 truncation.
(ii) \emph{Higher-genus topological entanglement}: the
Kitaev--Preskill formula generalises to higher genera via the
Lyubashenko--Virelizier mapping-class-group representation; the
precise correction to the Calabrese--Cardy entanglement from the
genus-$g$ state space is conjectured to be
$-2g\gamma_N + \log|B_{10}^{\mathrm{Maass}}(g)|$ at finite PBW stage,
subject to chain-level verification.
(iii) \emph{Holographic-code interpretation}: the identification of
$\gamma_N$ (or $\gamma_\infty$ after trace-class completion) with the
bulk derived-centre volume
(Remark~\ref{rem:ent-topological-entanglement-derived-centre})
is separate from the Knill--Laflamme condition
(Proposition~\ref{prop:ent-kl-scope}); a precise theorem requires
matching the non-semisimple MTC ribbon structure with a holographic
tensor network, a physical inner product, and an error algebra.
\end{remark}
