% !TEX root = ../../main.tex
% =====================================================================
% Chapter: Grand Unification; The Chiral Bar--Cobar Adjunction
%
% A typed conditional assembly theorem for the bar--cobar lane
%
% $\Omega^{\mathrm{ch}} \dashv B^{\mathrm{ch}}$
% on $\BrMon^{\mathrm{comp}}_\infty$
%
% whose unit/counit assemble Theorems A, B, C, D, H only after the
% signed log-FM, firewall, completion, trace, OCA, and comparison
% packages have been supplied. The three avatars
%
% L1 = chain-level ensemble (genus-$g$ trace on $U_\cA$)
% L2 = non-Tannakian categorical bar-cobar
% L3 = $(\infty,1)$-adjunction on braided conilpotent factorisation
% coalgebras
%
% are three presentations on their common comparison domain.
%
% Conventions:
% - $U_\cA := \cA \bowtie \cA^!_\infty$ conditional envelope
% (Drinfeld-double-type factorisation bialgebra: bowtie denotes
% factorisation-matched twist, not set-theoretic join)
% - $\BrMon^{\mathrm{comp}}_\infty$ = presentable $\infty$-category
% of conilpotent braided monoidal compact-generated presheaves on
% $\overline{\Conf}(X)$; equivalently, factorisation $\infty$-
% coalgebras on the Ran-compactified configuration space (Lurie
% HA~5.2; Francis-Gaitsgory chiral Koszul; Costello--Gwilliam II)
% - $\Phi_d^{(\Sigma_{d-1},C)}$ = two-stage CY$_d$-to-chiral specialization (Vol III: ch:cy-to-chiral);
% Rozansky-Witten category $\RW_4$ is the genuine output of
% $\Phi_4|_{\mathrm{HK}}$ on hyperkaehler targets.
% - Native-$E_n$ vs derived-$E_n$: native-$E_n$ is the structure
% inherited from factorisation; derived-$E_n$ is the structure
% exhibited by the derived centre. These never coincide on
% non-formal inputs; the Grand Theorem tracks both.
% =====================================================================

\providecommand{\BrMon}{\mathsf{BrMon}}
\providecommand{\BrMoncomp}{\BrMon^{\mathrm{comp}}_{\infty}}
\providecommand{\Coalg}{\mathsf{Coalg}}
\providecommand{\FactCoalg}{\Coalg^{\mathrm{fact}}_{\mathrm{conil}}}
\providecommand{\FactAlg}{\mathsf{ChirAlg}}
\providecommand{\BCh}{B^{\mathrm{ch}}}
\providecommand{\OmCh}{\Omega^{\mathrm{ch}}}
\providecommand{\Uch}{U^{\mathrm{ch}}}
\providecommand{\RW}{\mathsf{RW}}
\providecommand{\HK}{\mathrm{HK}}
\providecommand{\trgenus}{\mathrm{tr}_{g}}
\providecommand{\unitcounit}{\eta \dashv \varepsilon}
\providecommand{\cZch}{\cZ^{\mathrm{der}}_{\mathrm{ch}}}
\providecommand{\barBch}{\bar B^{\mathrm{ch}}}
\providecommand{\Confbar}{\overline{\Conf}}
\providecommand{\ChirHoch}{\mathrm{ChirHoch}}
\providecommand{\kappader}{\kappa}
\providecommand{\Phich}{\Phi^{\mathrm{ch}}}
\providecommand{\Psich}{\Psi^{\mathrm{ch}}}
\providecommand{\Vrep}{\mathsf{Rep}}
\providecommand{\locsys}{\mathrm{LocSys}}
\providecommand{\DMod}{\mathcal{D}}
\providecommand{\BarOrd}{B^{\mathrm{ord}}}
\providecommand{\ChapterIntro}[1]{\par\noindent\textit{#1}\par\medskip}

\chapter{Grand Unification: One Adjunction, Five Theorems, Three Avatars}
\label{chap:grand-unification-platonic}
\index{grand unification!bar-cobar adjunction|textbf}
\index{chiral bar-cobar!universal property|textbf}
\index{braided conilpotent factorisation coalgebras|textbf}
\index{L1 avatar (chain-level ensemble)|textbf}
\index{L2 avatar (non-Tannakian categorical bar-cobar)|textbf}
\index{L3 avatar ($\infty$-categorical adjunction)|textbf}

\ChapterIntro{Theorems A, B, C, D, H and the three avatars L1, L2,
L3 meet only after the source and target of each map have been fixed.
The ordered bar coalgebra, the Verdier--Koszul dual, the derived
chiral centre, the physical bulk, and the scalar modular shadow are
different objects. The adjunction
\[
 \OmCh \;\dashv\; \BCh
 \colon
 \FactAlg_X
 \rightleftarrows
 \BrMoncomp_X
\]
organises the bar--cobar lane. It does not by itself construct the
signed logarithmic Fulton--MacPherson cooperad, the completed
Positselski tower, the open--closed comparison, or the
Calabi--Yau-to-chiral comparison. This chapter records the exact
hypothesis packages under which the separate theorem surfaces assemble
into one typed diagram.}

\section{The Grand Theorem}
\label{sec:grand-theorem}

\subsection{Statement}
\label{ssec:grand-theorem-statement}

\begin{theorem}[Typed assembly theorem for chiral bar--cobar]
\label{thm:grand-unification-platonic}
\ClaimStatusConditional
\textup{[Type: Open, Cat\&Chain, levels $1$--$5$, hypothesis package
$\mathrm{LF}+\mathrm{FW}+H_A+\mathrm{CP}+H_H+H_D+\mathrm{OCA}+H_{L2}$.]}
Fix a smooth projective curve $X/\CC$ and an augmented,
conformal-weight filtered $E_1$-chiral algebra $\cA$ on $X$ with
finite-dimensional weight windows. Assume the following packages.
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Signed log-FM package $\mathrm{LF}$.} The relative
logarithmic Fulton--MacPherson chains form a modular cooperad
$C^{\log\mathrm{FM}}_{\mathrm{mod}}(X)$ with cocompositions
\[
 \Delta_\Gamma^{\log}=(\nu_\Gamma)_*\circ i_\Gamma^!
\]
including determinant-line signs, automorphism normalisations, Gysin
residue maps, proper pushforwards, and homotopy-coherent
coassociativity. With these signs the modular differential
$D_{\mathrm{mod}}^{\log}$ satisfies
$(D_{\mathrm{mod}}^{\log})^2=0$.
\item \emph{Firewall package $\mathrm{FW}$.} Every comparison uses the
five-object firewall of Convention~\ref{conv:master-five-object-firewall}:
\[
 \cA,\quad B^{\ord}(\cA),\quad
 \cA^{\mathrm i}=H^\bullet B^{\ord}(\cA),\quad
 \cA^!,\quad Z^{\der}_{\ch}(\cA).
\]
The counit $\OmCh B^{\ord}(\cA)\to\cA$ is bar--cobar inversion;
Verdier duality produces $\cA^!$; Hochschild cochains produce
$Z^{\der}_{\ch}(\cA)$. These arrows are not interchangeable.
\item \emph{Theorem A package $H_A$.} The hypotheses of
Theorem~\ref{thm:koszul-reflection} hold: augmentation,
augmentation-ideal completion, finite-dimensional conformal-weight bar
pieces, and the weight-completed/pro-conilpotent ambient for
class~$\mathsf M$.
\item \emph{Completed Positselski package $\mathrm{CP}$.} The finite
weight windows of the chiral bar coalgebra form a strict
Mittag--Leffler tower satisfying \textup{(CP1)--(CP3)} of
Theorem~\ref{thm:chiral-positselski-weight-completed}. In particular
all Milnor $\varprojlim^1$ terms in the co/contra comparison are
controlled.
\item \emph{Theorem H package $H_H$.} The PBW--Koszul, perfectness,
genericity, completion, and Arnold--Orlik--Solomon contraction
hypotheses of Theorem~\ref{thm:main-koszul-hoch} hold, or else the
collision-depth defect complex $K^\bullet_{\mathrm{DH}}(\cA)$ is
specified and proved acyclic in the stated ambient.
\item \emph{Trace package $H_D$.} The modular trace is defined on the
signed log-FM cooperad, is compatible with clutching, and is restricted
to the uniform-weight scalar lane whenever the formula
$\mathrm{obs}_g=\kappa(\cA)\lambda_g$ is asserted without a
cross-channel correction.
\item \emph{Comparison packages.} The physical-bulk reading requires
the open--closed algebra comparison
$\mathrm{OCA}$:
$\mathcal O^{\mathrm{phys}}_{\mathrm{bulk}}(\cA)
\xrightarrow{\sim} Z^{\der}_{\ch}(\cA)$. The categorical and
Calabi--Yau faces require the two-stage functor
$\Phi_d^{(\Sigma_{d-1},C)}
=\SpCh_{\Sigma_{d-1},C}\circ\PhiFA_d$ with its gerbe, Hall,
completion, and descent hypotheses; call this package $H_{L2}$.
\end{enumerate}

Then the bar--cobar lane carries the presentable
$\infty$-categorical adjoint pair
\begin{equation}
\label{eq:grand-adjunction-platonic}
 \OmCh \;\dashv\; \BCh
 \colon\;
 \FactAlg_X
 \;\rightleftarrows\;
 \BrMoncomp_X,
\end{equation}
with left adjoint the chiral cobar construction and right adjoint the
chiral bar construction, and the following typed readouts are valid.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Ordered twisting morphism.} The unit and counit of
\eqref{eq:grand-adjunction-platonic} are represented, on the ordered
chain presentation, by the universal Maurer--Cartan element
\[
 \Theta_\cA\in
 \mathrm{Conv}\bigl(B^{\ord}(\cA),\cA\bigr),
 \qquad
 D\Theta_\cA+\tfrac12[\Theta_\cA,\Theta_\cA]=0,
\]
with $D^2=0$ on the modular logarithmic enhancement only under
$\mathrm{LF}$.
\item \emph{Koszul duality locus.} The full $\infty$-subcategory
$\FactAlg^{\mathrm{Kos}}_X \subset \FactAlg_X$ on which $\varepsilon$
is an equivalence is presented by chirally Koszul algebras and
carries a symmetric duality $\cA \mapsto \cA^!$ induced from
Verdier dualisation of factorisation $\DMod$-modules;
equivalently $\BCh$ restricts there to an equivalence of
presentable stable $\infty$-categories under $H_A$.
\item \emph{Positselski coderived inversion.} The cobar image
$\OmCh(\BCh(\cC))$ is naturally equivalent to $\cC$ in the completed
coderived/contraderived ambient supplied by $\mathrm{CP}$. This is a
finite-window or strict-completed statement; for class~$\mathsf M$ the
raw direct-sum statement is false.
\item \emph{Derived centre complementarity.} The composite
$\BCh \circ \OmCh \colon \BrMoncomp_X \to \BrMoncomp_X$ carries a
canonical natural transformation to the Hochschild functor
$\cC \mapsto \cZch(\OmCh(\cC))$ whose scalar invariant is the pair
$(\kappa,\kappa^!)$ of family-dependent constants
$\kappa + \kappa^! \in \{0,\,13,\,250/3,\,98/3\}$ recorded in
Chapter~\ref{ch:landscape-census} on the four standard classes
G / L / C / M. This is the scalar readout of a trace on the
derived-centre lane, not an identification of $B^{\ord}(\cA)$ with
$Z^{\der}_{\ch}(\cA)$.
\item \emph{Obstruction-tower universality.} For every genus $g\geq 0$,
the genus-$g$ trace
\begin{equation}
\label{eq:genus-g-trace-platonic}
 \trgenus \colon
 \BCh(\cA)
 \;\longrightarrow\;
 H^\ast(\overline{\cM}_{g,n},\CC)
\end{equation}
obtained by fibre integration of the universal twisting morphism
along $\overline{\cM}_{g,n} \to \mathrm{pt}$ factors through a
single class in
$H^2(\overline{\cM}_{g,n},\CC)$ proportional to $\kappa(\cA)$, with
proportionality constant the $g$-th $\lambda$-class
$\lambda_g^{\mathrm{FP}}$; i.e.\
$\mathrm{obs}_g(\cA)=\kappa(\cA)\lambda_g$ on the
uniform-weight stratum and
\[
F_g(\cA)
=F_g^{\mathrm{sc}}(\cA)+\delta F_g^{\mathrm{cross}}(\cA),
\qquad
F_g^{\mathrm{sc}}(\cA)=\kappa(\cA)\lambda_g^{\mathrm{FP}},
\]
on the multi-weight scalar lane.
\item \emph{Hochschild concentration.} The chiral Hochschild object
$\ChirHoch^\bullet(\cA) := \cZch(\cA)$ is naturally equivalent, inside
the adjunction~\eqref{eq:grand-adjunction-platonic}, to the
endomorphism object
$\End_{\BrMoncomp_X}(\BCh(\cA))$; its cohomology is concentrated in
degrees $\{0,1,2\}$ under $H_H$. Outside $H_H$ the theorem asserts
only the specified obstruction complex $K^\bullet_{\mathrm{DH}}(\cA)$.
\item \emph{Three-avatar presentation.} The adjoint
pair~\eqref{eq:grand-adjunction-platonic} admits three canonical
presentations on the common domain where their comparison packages
hold:
\begin{itemize}
\item \emph{L1 (chain-level ensemble).} Presented on chain-complexes
 in the ordered-configuration model: $\BCh(\cA)$ is $\BarOrd(\cA) =
 T^c(s^{-1}\bar\cA)$ equipped with the Beilinson-Drinfeld
 factorisation differential; $\OmCh$ is the ordered cobar
 construction; unit/counit are the explicit Mittag-Leffler
 witnesses of Chapter~\ref{chap:bar-cobar} and
 Theorem~\ref{thm:chiral-positselski-weight-completed}.
\item \emph{L2 (non-Tannakian categorical).} Presented on the
 presentable stable $\infty$-category
 $\Vrep(\cA) := \cA\text{-}\mathsf{mod}^{\mathrm{fact}}$ as the
 bar--cobar reconstruction on braided module categories; the
 formal-locus restriction recovers the Tannakian reconstruction,
 while the non-formal complement is detected by $\RW_d$-type
 category-valued outputs of the Calabi--Yau specialization
 $\Phi_d^{(\Sigma_{d-1},C)}$ under $H_{L2}$. All four standard
 archetypes remain chirally Koszul; the non-Tannakian distinction tracks
 formality of the chiral $A_\infty$-structure, not Koszulness of
 the chiral bar complex.
\item \emph{L3 ($\infty$-categorical, genus-$g$).} Presented on the
 Lurie-Francis-Gaitsgory machinery \cite[HA~5.2]{LurieDAGX}, \cite{FG12}
 of factorisation $\infty$-operads with values in presentable
 stable $\infty$-categories; the genus-$g$ trace is the homotopy
 fixed-point spectrum of the $S^1$-action on $\Uch_\cA :=
 \cA \bowtie_{\infty} \cA^!_\infty$ restricted to
 $\overline{\cM}_{g,n}$ only after the universal-envelope and trace
 packages have been supplied.
\end{itemize}
No clause promotes a scalar shadow to an operator algebra, a bar
coalgebra to a bulk, or a recognition target to a constructed object.
\end{enumerate}
\end{theorem}

\begin{remark}[Exact construction packages still missing]
\label{rem:gu-missing-packages}
\ClaimStatusConditional
The theorem is an assembly theorem, not a proof that all packages
exist in full generality. The remaining mathematical work needed for
the unrestricted version is explicit:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item construct the signed relative log-FM modular cooperad, including
orientation lines, Gysin residues, proper pushforwards, automorphism
normalisations, and homotopy-coherent coassociativity;
\item prove \textup{(CP1)--(CP3)} for every class-$\mathsf M$ tower
used downstream, including the Hom-cone Mittag--Leffler calculation;
\item identify the Hochschild defect complex
$K^\bullet_{\mathrm{DH}}(\cA)$ off the PBW/generic locus and prove
acyclicity before claiming concentration;
\item construct OCA whenever the derived chiral centre is read as the
physical bulk;
\item construct the Hall--Borcherds chain datum
$(\beta,\delta,\varepsilon,\tau)$ before promoting $\Delta_5$ from a
scalar denominator to an operator-level theorem;
\item prove the two-stage CY-to-chiral functor
$\SpCh_{\Sigma_{d-1},C}\circ\PhiFA_d$ with completion, gerbe, and
descent data before using L2 as a theorem rather than a recognition
target.
\end{enumerate}
\end{remark}

\subsection{The five theorem corollaries}
\label{ssec:grand-theorem-five-corollaries}

\begin{corollary}[Theorem~A is the adjunction itself]
\label{cor:gu-theorem-a-platonic}
\ClaimStatusConditional
Under the Theorem A package $H_A$, the bar--cobar clause of
Theorem~\ref{thm:grand-unification-platonic} is exactly
Theorem~\ref{thm:koszul-reflection}: the ordered chiral bar functor
is right adjoint to the ordered chiral cobar functor, and the counit
\[
 \OmCh_X B^{\ord}_X(\cA)\longrightarrow \cA
\]
is a quasi-isomorphism on the Koszul/complete locus.
\end{corollary}

\begin{proof}
Theorem~\ref{thm:koszul-reflection} supplies the Hom-bijection, the
universal twisting morphism, and the counit quasi-isomorphism under
augmentation, completion, and finite-window hypotheses. The assembly
theorem imports exactly those hypotheses as $H_A$ and adds no raw
class-$\mathsf M$ direct-sum statement.
\end{proof}

\begin{corollary}[Theorem~B is Positselski localisation]
\label{cor:gu-theorem-b-platonic}
\ClaimStatusConditional
Under the completed Positselski package \textup{(CP1)--(CP3)},
Theorem~B is property~\textup{(iii)} of
Theorem~\ref{thm:grand-unification-platonic}:
\[
\OmCh_X(\BCh_X(\cC)) \simeq \cC
\]
in the completed coderived/contraderived chiral ambient. It is not a
raw direct-sum theorem for class~$\mathsf M$.
\end{corollary}

\begin{proof}
Theorem~\ref{thm:chiral-positselski-weight-completed} proves the
continuous co/contra comparison on strict Mittag--Leffler completed
towers. Chapter~\ref{ch:theorem-B-scope-platonic} also proves that
the raw class-$\mathsf M$ direct-sum reading fails; therefore the
assembly theorem inherits precisely the completed scope.
\end{proof}

\begin{corollary}[Theorem~C is the scalar invariant of the double]
\label{cor:gu-theorem-c-platonic}
\ClaimStatusConditional
Theorem~C (derived-centre complementarity: $\kappa + \kappa^! \in
\{0,13,250/3,98/3\}$ on the classical four-archetype
$\mathsf{G}/\mathsf{L}/\mathsf{C}/\mathsf{M}$ landmark ceiling;
enlarged to the canonical five-archetype bucket
$\{0,8,13,250/3,98/3\}$ by the Vol~III $\mathsf{B}$-row
$\mathcal{H}_{\mathrm{Muk}}(K3)$ at $K^\kappa = 8$, per
Convention~\ref{conv:theorem-c-bucket}) is property~(iv) of
Theorem~\ref{thm:grand-unification-platonic}, restricted to each
archetype standard witness.
\end{corollary}

\begin{proof}
Chapter~\ref{ch:landscape-census} and
Chapter~\ref{ch:theorem-C-refinements-platonic} compute the listed
scalar values on their family witnesses. The present corollary says
only that these scalar values are read from the derived-centre trace
lane once the firewall and trace hypotheses of
Theorem~\ref{thm:grand-unification-platonic} are imposed. The scalar
calculation does not identify $B^{\ord}(\cA)$ with
$Z^{\der}_{\ch}(\cA)$.
\end{proof}

\begin{corollary}[Theorem~D is obstruction-tower universality]
\label{cor:gu-theorem-d-platonic}
\ClaimStatusConditional
Theorem~D (obstruction-tower universality
$\mathrm{obs}_g(\cA)=\kappa(\cA)\lambda_g$) is property~(v) of
Theorem~\ref{thm:grand-unification-platonic} on the signed log-FM
uniform-weight scalar lane. On the multi-weight lane the asserted
formula is
\[
F_g(\cA)=F_g^{\mathrm{sc}}(\cA)
       +\delta F_g^{\mathrm{cross}}(\cA),
\qquad
F_g^{\mathrm{sc}}(\cA)=\kappa(\cA)\lambda_g^{\mathrm{FP}}.
\]
\end{corollary}

\begin{proof}
Chapter~\ref{ch:higher-genus} proves the scalar formula on the
uniform-weight lane and records the cross-channel correction on the
multi-weight lane. The assembly theorem imports the trace and
clutching hypotheses as $H_D$, so the corollary has exactly that
scope.
\end{proof}

\begin{corollary}[Theorem~H is Hochschild concentration]
\label{cor:gu-theorem-h-platonic}
\ClaimStatusConditional
Theorem~H (chiral Hochschild concentration
$\ChirHoch^\bullet(\cA)$ lives in $\{0,1,2\}$) is property~(vi) of
Theorem~\ref{thm:grand-unification-platonic} on its proved surface.
\end{corollary}

\begin{proof}
Property~(vi) names the endomorphism object
$\End_{\BrMoncomp_X}(\BCh(\cA))$ as the chiral Hochschild object;
the concentration in degrees $\{0,1,2\}$ is Theorem~H on the
Koszul/generic surface, proved in
Theorem~\ref{thm:theorem-h-on-koszul-locus} and
Chapter~\ref{chap:three-hochschild-unification}. The logarithmic and
critical-level formulae of
Chapter~\ref{chap:theorem-h-off-koszul-platonic} are boundary
surfaces with the conditional hypotheses recorded there.
\end{proof}

\subsection{The three-avatar corollaries (L1, L2, L3)}
\label{ssec:grand-theorem-three-avatars}

\begin{corollary}[L1; chain-level ensemble via genus-$g$ trace]
\label{cor:gu-L1-platonic}
\ClaimStatusConditional
Under $\mathrm{LF}$, $H_A$, $\mathrm{CP}$, and $H_D$, the L1 avatar is
the ordered chain presentation of the bar--cobar lane, evaluated by
the modular trace along $\overline{\cM}_{g,n}\to\mathrm{pt}$. On that
scope the displayed identity is
\begin{equation}
\label{eq:L1-avatar-platonic}
 \trgenus \!\left( \OmCh(\BCh(\cA)) \right)
 \;=\;
 \int_{\overline{\cM}_{g,n}} \Theta_{\cA}^{\wedge g}
 \;=\;
 F_g(\cA).
\end{equation}
\end{corollary}

\begin{proof}
The ordered chain model gives $\BCh(\cA)=B^{\ord}(\cA)$ and
$H_A+\mathrm{CP}$ supplies the completed counit comparison. The trace
package $H_D$ is exactly the extra datum required to integrate
$\Theta_\cA^{\wedge g}$ over the modular boundary. Without $H_D$ the
left side remains a bar--cobar object and no genus-$g$ scalar
identity follows.
\end{proof}

\begin{corollary}[L2; non-Tannakian categorical bar--cobar]
\label{cor:gu-L2-platonic}
\ClaimStatusConditional
On the $H_{L2}$ comparison domain and on the non-formal complement,
the $\infty$-adjunction restricts to
a categorical bar--cobar adjunction
\[
 \OmCh^{\mathrm{cat}} \;\dashv\; \BCh^{\mathrm{cat}}
 \colon
 \mathsf{BrCat}^{\mathrm{cat}}_X
 \;\rightleftarrows\;
 \mathsf{BrCat}^{\mathrm{cat,cocomp}}_X
\]
on braided monoidal $\infty$-categories of factorisation modules. In
this domain the formal locus maps to the Tannakian fixed locus. The
non-Tannakian stratum is detected by failure of the categorical bar to
be fibrewise semisimple; the Rozansky-Witten category $\RW_4$ is the
genuine output of $\Phi_4|_{\HK}$ in the constructed hyperkaehler
cases, with non-Tannakian character witnessed, not classified, by the
failure of $\RW_4$ to admit an exceptional collection. All standard
archetypes remain chirally Koszul throughout; the
non-Tannakian comparison tracks formality of the chiral
$A_\infty$-structure, not Koszulness of the bar complex.
\end{corollary}

\begin{proof}[Proof sketch and scope]
The categorical bar--cobar of Francis-Gaitsgory
$(\infty,1)$-operadic machinery \cite{FG12} restricts to
$\BrMoncomp_X$ by the presentability of
$\cA\text{-}\mathsf{mod}^{\mathrm{fact}}$; the non-Tannakian
stratum is detected, on the $H_{L2}$ comparison domain, by the
complement of the locus where fibrewise exact $\otimes$-functors into
$\Vrep_\infty$ are representable. On the hyperkaehler targets for
which the Vol~III chiral-to-CY functor $\Phi_4$ has been constructed,
the Rozansky-Witten category $\RW_4$ gives the concrete witness; the
absence of an exceptional collection is supporting evidence, not an
if-and-only-if criterion.
\end{proof}

\begin{corollary}[L3; $(\infty,1)$-categorical adjunction]
\label{cor:gu-L3-platonic}
\ClaimStatusConditional
The Lurie-Francis-Gaitsgory
$(\infty,1)$-presentation of bar--cobar
\cite[HA~5.2.3]{LurieDAGX}, \cite{FG12} is property~(vii.L3) of
Theorem~\ref{thm:grand-unification-platonic}; the two presentations
L1 and L3 are related by factorisation Dold-Kan
\cite[HA~1.2.3]{Lurie17} on their common completed finite-window
domain, and L2 sits between them only under the comparison package
$H_{L2}$.
\end{corollary}

\section{Proof of the Grand Theorem}
\label{sec:grand-theorem-proof}

\subsection{What is assembled}
\label{ssec:grand-theorem-new-content}

The theorem does not assert that a single presentability argument
constructs every object in the programme. It assembles already named
lanes after their hypotheses have been supplied. Clause~(i) is the
ordered Maurer--Cartan bar lane. Clause~(ii) is the Koszul locus of
Theorem~\ref{thm:koszul-reflection}. Clause~(iii) is the completed
Positselski theorem of
Theorem~\ref{thm:chiral-positselski-weight-completed}. Clause~(iv) is
the scalar Theorem~C read through the five-object firewall. Clause~(v)
is Theorem~D on the trace lane. Clause~(vi) is Theorem~H under its PBW
and completion hypotheses. Clause~(vii) records the L1/L2/L3
comparison only on the common domain where the comparison packages
exist.

\begin{proof}[Proof of Theorem~\ref{thm:grand-unification-platonic}]
\emph{Step 1: the bar--cobar adjunction.}
Theorem~\ref{thm:koszul-reflection} and the Francis--Gaitsgory
universal twisting property \cite[\S6]{FG12} give the adjunction
\eqref{eq:grand-adjunction-platonic} in the ordered, augmented,
complete chiral ambient. The finite-window and completion hypotheses
in $H_A$ are exactly the hypotheses under which the counit is a
quasi-isomorphism.

\emph{Step 2: modular logarithmic enhancement.}
The ordered bar differential satisfies the Maurer--Cartan equation on
the fixed-curve Ran model. Passing to modular logarithmic families
adds the planted-forest, collision, sewing, and trace terms. The
assumption $\mathrm{LF}$ supplies the missing determinant-line signs,
Gysin residues, proper pushforwards, automorphism normalisations, and
homotopy-coherent coassociativity; hence
$(D_{\mathrm{mod}}^{\log})^2=0$ is available exactly on that surface.

\emph{Step 3: completed inversion.}
Theorem~\ref{thm:chiral-positselski-weight-completed} identifies the
completed coderived comodule category with the completed
contraderived contramodule category after \textup{(CP1)--(CP3)}. This
is the only scope in which class~$\mathsf M$ is used in clause~(iii);
the raw direct-sum failure is excluded by hypothesis.

\emph{Step 4: centre, trace, and scalar lanes.}
Convention~\ref{conv:master-five-object-firewall} separates
bar--cobar inversion, Verdier duality, and Hochschild centre
formation. The scalar constants of Theorem~C are imported from
Chapter~\ref{ch:landscape-census}; the trace formula of Theorem~D is
imported from Chapter~\ref{ch:higher-genus}; and Theorem~H is imported
from Theorem~\ref{thm:main-koszul-hoch}. Each import is made only with
its corresponding package $H_H$ or $H_D$.

\emph{Step 5: comparison faces.}
OCA converts the derived centre into a physical bulk when such a
statement is made. The L2 face is supplied by $H_{L2}$ and by
Theorem~\ref{thm:L2-chain-level-gerbe-platonic}; without it, the
non-Tannakian and Calabi--Yau faces are recognition targets rather
than consequences of the bar--cobar adjunction.
\qedhere
\end{proof}

\subsection{Primary references for the $\infty$-categorical surface}
\label{ssec:grand-theorem-primary-references}

The proof uses: Lurie \cite[Higher Algebra~5.2, 5.5]{Lurie17} for
presentable $\infty$-adjoint-functor theory and Dold-Kan; Francis-
Gaitsgory \cite{FG12} for the chiral Koszul duality adjunction at
the $(\infty,1)$-categorical level; Costello-Gwilliam \cite{CG17,CG-vol2}
for the factorisation-algebra presentation on the curve~$X$. The
chain-level witnesses are the standard Beilinson-Drinfeld
\cite{BD04} presentation.

\section{Avatar corollaries expanded}
\label{sec:avatar-corollaries-expanded}

\subsection{L1 as a trace identity on the universal envelope}
\label{ssec:L1-trace-identity}

\begin{proposition}[L1 trace identity]
\label{prop:L1-trace-identity-platonic}
\ClaimStatusConditional
Assume the universal-envelope comparison, the trace package $H_D$, and
the completion packages of Theorem~\ref{thm:grand-unification-platonic}.
Then the genus-$g$ trace of the envelope
$\Uch_\cA := \cA \bowtie \cA^!_\infty$, when this envelope has been
constructed, agrees with the chain-level integration of
$\Theta_\cA$ along $\overline{\cM}_{g,n}$:
\begin{equation}
\label{eq:L1-trace-identity-platonic}
 \trgenus(\Uch_\cA)
 \;=\;
 F_g(\cA)
 \;=\;
 \kappa(\cA)\,\lambda_g^{\mathrm{FP}}
 \;+\;
 \delta F_g^{\mathrm{cross}},
\end{equation}
with $\delta F_g^{\mathrm{cross}}$ the cross-modular correction
that vanishes on the uniform-weight stratum.
\end{proposition}

\begin{proof}
The universal-envelope comparison supplies the object
$\Uch_\cA$ and the map from its trace to the ordered bar trace. The
trace package $H_D$ supplies integration over the signed modular
log-FM boundary. Theorem~D then gives the displayed scalar term on the
uniform-weight lane and the cross-channel correction on the
multi-weight lane.
\end{proof}

\subsection{L2 as the non-Tannakian recognition surface}
\label{ssec:L2-non-tannakian}

On the $H_{L2}$ comparison domain the non-Tannakian stratum is read
through the locus on which $\Phi_d^{(\Sigma_{d-1},C)}$ produces
category-valued outputs (Vol~III, chapter
\texttt{cy\_to\_chiral.tex}). For $d = 4$ in the constructed
hyperkaehler cases, $\Phi_4^{(\Sigma_3,C)}|_{\HK}$ produces $\RW_4$,
the Rozansky-Witten category; failure of an exceptional collection is
a witness for non-Tannakian behaviour, not a classification theorem.

\begin{proposition}[Non-Tannakian projection]
\label{prop:L2-non-tannakian-platonic}
\ClaimStatusConditional
Conditional on Conjecture~$\Pi_3^{\mathrm{ch}}$ of
Vol~III (chain-level CY-A$_3$), the non-Tannakian stratum of L2
is detected by the conditional image of the non-formal CY$_d$ targets
$T$, i.e.\ the targets for which
$\Phi_d^{(\Sigma_{d-1},C)}(T)$ is not fibrewise exact-Tannakian.
Formality of the chiral $A_\infty$-structure, not Koszulness of the
bar complex, is the distinguishing criterion; all four archetypes
G / L / C / M remain chirally Koszul.
\end{proposition}

\begin{proof}[Proof sketch]
Under $\Pi_3^{\mathrm{ch}}$, the CY$_3$-to-chiral correspondence
$\Phi_3^{(\Sigma_2,C)}=\SpCh_{\Sigma_2,C}\circ\PhiFA_3$
is defined on chain-level; its output is chirally formal on the
constructed formal comparison locus (classes G and L), and non-formal
on the constructed non-formal comparison locus (classes C and M). All
four outputs remain chirally Koszul. The formality-locus
restriction of L2 recovers the Tannakian stratum on this comparison
domain; the non-formal complement supplies the detected
non-Tannakian stratum. The Rozansky-Witten category is the witness for
$d=4$ on the constructed hyperkaehler targets.
\end{proof}

\subsection{L3 as a presentable $\infty$-category adjunction}
\label{ssec:L3-infinity}

The L3 presentation is the most flexible for stating universal
properties. The adjunction $\OmCh \dashv \BCh$ in L3 form is
characterised by the $\infty$-universal property: $\BCh(\cA)$ is
the classifying object for conilpotent braided factorisation
coalgebras receiving a chiral twisting morphism from $\cA$. This is
the $(\infty,1)$-categorical statement for the bar--cobar lane. The
trace, centre, physical-bulk, and CY comparison faces enter only
through the packages named in
Theorem~\ref{thm:grand-unification-platonic}.

\section{The typed assembly diagram}
\label{sec:single-infty-adjunction}

Theorem~\ref{thm:grand-unification-platonic} fixes the common
bar--cobar spine:
$\infty$-adjunction
\[
 \OmCh \;\dashv\; \BCh
 \colon\;
 \FactAlg_X
 \;\rightleftarrows\;
\BrMoncomp_X,
\]
whose domain is chiral algebras on $X$, whose codomain is
braided conilpotent factorisation coalgebras on $\Confbar(X)$, and
whose unit/counit control the inversion lane. The categorical target
(L2), the chain-level trace (L1), and the genus-$g$ categorical trace
(L3) are comparison faces of this spine only after their listed
hypotheses have been supplied.

\subsection{Three-volume corollary of the Grand Theorem}
\label{ssec:three-volume-corollary}

\begin{corollary}[Three volumes, three faces of the adjunction]
\label{cor:three-volume-platonic}
\ClaimStatusConditional
The three Volumes of the chiral bar--cobar theory develop
complementary faces of the
adjunction~\eqref{eq:grand-adjunction-platonic}, each using both
L1 and L3 presentations and restricting the categorical face L2
to a different geometric locus. This is a conditional comparison
statement: the Volume~I and Volume~II faces below are valid in their
stated scopes, and the Volume~III CY$_3$ gerbe-twisted face has
exactly the conditional strength of
Theorem~\ref{thm:L2-chain-level-gerbe-platonic}. Volume~I develops the chain-level
(L1) and $(\infty,1)$-categorical (L3) presentations on a smooth
projective curve $X$, with the ordered bar complex
$\BarOrd(\cA) = T^c(s^{-1}\bar\cA)$ as the chain-level anchor.
Volume~II develops the L3 presentation on
$\mathrm{SC}^{\mathrm{ch,top}}$-algebras over
$\Confbar(X) \times \bR^k$, with transverse topological structure
extending the L3 machinery. Volume~III develops L2 in the
CY-to-chiral direction via the two-stage specialization
$\Phi_d^{(\Sigma_{d-1},C)}$, and is the source
of the non-Tannakian stratum of L2 as
Theorem~\ref{thm:L2-chain-level-gerbe-platonic} exhibits for $d = 3$.
\end{corollary}

\begin{proof}
The statement is obtained by applying the three comparison corollaries
with their hypotheses left visible. Volume~I supplies the ordered
chain model and the completed bar--cobar adjunction. Volume~II enters
only after the transverse topological $\SCchtop$ comparison is
provided. Volume~III enters only through
$\Phi_d^{(\Sigma_{d-1},C)}$ and the gerbe-twisted L2 package of
Theorem~\ref{thm:L2-chain-level-gerbe-platonic}. Thus the corollary
records a diagram of conditional restrictions, not a new
unconditional equivalence between the three volumes.
\end{proof}

\section{Independent verification (multi-path)}
\label{sec:grand-theorem-verification}

The numerical inputs imported into the typed assembly have their own
verification sources. The assembly itself remains conditional on the
packages in Theorem~\ref{thm:grand-unification-platonic}.
\begin{itemize}
\item \emph{Verification of property~(i).} Chain-level: the
universal twisting morphism $\Theta_\cA$ is constructed explicitly
in Chapter~\ref{chap:bar-cobar}.
$(\infty,1)$-categorical: the same is presented as the unit of
$\OmCh \dashv \BCh$ in \cite[\S6]{FG11}.
Cross-check: the Francis-Gaitsgory universal property \cite[Thm~6.3]{FG12}.
\item \emph{Verification of property~(iii).} Chain-level: the
Positselski coderived inversion is proved on chain-complexes in
Chapter~\ref{ch:theorem-B-scope-platonic}. $(\infty,1)$-categorical:
the same localisation is the Lurie Dwyer-Kan equivalence
\cite[HA~1.3]{LurieDAGX}. Cross-check: the Keller-Lefevre duality
\cite{Keller01} on the Koszul locus.
\item \emph{Verification of property~(iv).} The classical
four-archetype constants
$\kappa + \kappa^! \in \{0,13,250/3,98/3\}$ on
$\mathsf{G}/\mathsf{L}/\mathsf{C}/\mathsf{M}$ are computed
independently on the four archetypes by: (a) direct trace-form
calculation, (b) central-charge arithmetic, (c) shadow-tower
depth from Chapter~\ref{chap:shadow-tower-extended-families},
(d) BV-BRST ghost computation. All four paths agree in
Chapter~\ref{ch:landscape-census}. The canonical five-element
bucket $\{0,8,13,250/3,98/3\}$ adjoins the $\mathsf{B}$-row
Mukai doubling witness via the Beilinson--Drinfeld Koszul-conductor
identity; see Convention~\ref{conv:theorem-c-bucket}.
\item \emph{Verification of property~(v).} The formula
$\mathrm{obs}_g(\cA)=\kappa(\cA)\lambda_g$ is proved on the
uniform-weight stratum in Chapter~\ref{ch:higher-genus};
independent verifications at genus~1 are in
Chapter~\ref{ch:genus1-seven-faces} and at higher genus in
Chapter~\ref{chap:clutching-uniqueness-socle}.
\item \emph{Verification of property~(vi).} The Hochschild
concentration is proved on the Koszul/generic surface in
Theorem~\ref{thm:theorem-h-on-koszul-locus} and
Chapter~\ref{chap:three-hochschild-unification}; independent
verification via Costello-Gwilliam \cite{CG17} gives the same
bounds on that surface.
\end{itemize}

\section{Open threads}
\label{sec:grand-theorem-open-threads}

The L1 and L3 faces close only on the completed finite-window domain
specified above. The L2 face is a comparison target until the
Costello--Li curved-HKR transfer \cite{CL20}, the gerbe/descent
package, and the two-stage CY-to-chiral specialization have been
constructed for the chosen compact CY$_3$ target. The theorem below
records that conditional chain-level scope; Vol~III
(\texttt{cy\_to\_chiral.tex}) contains the corresponding CY-side
formulation.

\begin{theorem}[L2 chain-level functor into gerbe-twisted braided monoidal $\infty$-category]
\label{thm:L2-chain-level-gerbe-platonic}
\ClaimStatusConditional
Let $X$ be a compact CY$_3$ without a full exceptional collection
(Bondal-Van den Bergh non-representability \cite{BondalVdB03});
let $\alpha_X \in H^3(X,\CC^\times)$ denote the Brauer-type gerbe
class obstructing strictification of the braided $\infty$-category
of perfect complexes to an honest bialgebra; let
$\mathrm{HKR}_\infty^{\mathrm{curv},\hbar}$ denote the
curved-$L_\infty$ quasi-isomorphism of Costello-Li \cite{CL20}.
Conditional on the BCOV transfer of \cite{CL20} extending to the
genus range used on $X$, and on the gerbe/descent data of
\S\ref{ssec:pr-alpha-X-local-global}, there is a chain-level
$\infty$-functor
\begin{equation}
\label{eq:Phi-3-ch-platonic}
 \Phi_3^{\mathrm{ch}}
 \;\colon\;
 \mathrm{Perf}^{\mathrm{CY3}}_\infty(X)
 \;\longrightarrow\;
 \BrMoncomp_{X,\alpha_X}
\end{equation}
valued in the gerbe-twisted presentable $\infty$-category of
conilpotent braided-monoidal compact-generated factorisation
coalgebras on $\Confbar(X)$. The functor~\eqref{eq:Phi-3-ch-platonic}
satisfies three properties.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Chain-level realisation.} The underlying chain-level
model of $\Phi_3^{\mathrm{ch}}(X)$ is the explicit chain-level bar
$B^{\mathrm{cat}}(D^b(X))$ (\S~\ref{ssec:explicit-bar-model}),
with $L_\infty$-structure inherited from
$\mathrm{HKR}_\infty^{\mathrm{curv},\hbar}$ and with
gerbe-twisting $\alpha_X$ acting on the associator.
\item \emph{Gerbe compatibility.} The class
$\alpha_X \in H^3(X,\CC^\times)$ is the specified obstruction datum
for lifting $\Phi_3^{\mathrm{ch}}$ from the gerbe-twisted target
$\BrMoncomp_{X,\alpha_X}$ to $\BrMoncomp_X$. A strict untwisted lift
exists only after a separate descent computation trivialises this
class.
\item \emph{Categorical-H compatibility.} The ambient Hochschild
complex $\mathrm{ChirHoch}^\bullet(\Phi_3^{\mathrm{ch}}(X))$ is
equivalent to the Costello-Li BCOV ambient Hochschild complex,
concentrated in the three-step filtration of Theorem~H only under the
package $H_H$ of Theorem~\ref{thm:grand-unification-platonic}.
\end{enumerate}
Consequently, on the subcategory of compact CY$_3$ targets for
which the Costello-Li BCOV transfer and descent package are
established, the non-Tannakian stratum of the L2 avatar of
Theorem~\ref{thm:grand-unification-platonic} is detected by
the non-formal chain-level CY$_3$ targets in the conditional image of
$\Phi_3^{\mathrm{ch}}$.
\end{theorem}

\begin{proof}
\emph{Step 1 (lift the derived category to a chain-level $\infty$-functor).}
On a compact CY$_3$, $D^b(X)$ admits no full exceptional
collection \cite{BondalVdB03}, and the derived-to-bialgebra
construction via semiorthogonal decomposition fails. By
\cite[HA~5.1.2.2, 5.1.4.2]{LurieDAGX}, the $\infty$-category
$\mathrm{Perf}^{\mathrm{CY3}}_\infty(X)$ of perfect complexes on a
CY$_3$ is symmetric-monoidally enriched over
$(\Coalg^{\mathrm{fact}}_{\mathrm{conil}})_\infty$; its underlying
braided monoidal structure lands in $\BrMoncomp_X$ up to a
Brauer-type twist.

\emph{Step 2 (identify the gerbe obstruction).}
The Brauer-type twist is controlled by $H^3(X,\CC^\times)$, the
standard obstruction group for strictifying a braided
$\infty$-category to an honest bialgebra \cite{Toen07}, giving the
specified class $\alpha_X = [\mathrm{Gerbe}(\Phi_3)]$. A full
exceptional collection is a sufficient strictification datum in cases
where the semiorthogonal bialgebra construction is available; absence
of such a collection does not by itself compute $\alpha_X$. Thus the
target is $\BrMoncomp_{X,\alpha_X}$ until a separate descent
computation proves $\alpha_X=0$.

\emph{Step 3 (construct the $L_\infty$-structure via BCOV transfer).}
The Costello-Li curved $L_\infty$-quasi-isomorphism
$\mathrm{HKR}_\infty^{\mathrm{curv},\hbar}$ of \cite{CL20}
transfers the Dolbeault-BCOV $L_\infty$-structure on
$\mathrm{PV}^\bullet(X)[[\hbar]]$ to the chain-level
$\infty$-operadic structure on
$\mathrm{Perf}^{\mathrm{CY3}}_\infty(X)$ when the $H_{L2}$ transfer
datum has been supplied. The quintic discussion below records the
finite genus range used in the model calculation
(\S~\ref{ssec:BCOV-transfer-X5}); extension to another compact
CY$_3$ is part of the theorem's scope condition, not a consequence of
the local model alone. Combining with Step~2 gives the chain-level
$L_\infty$-data of
$\Phi_3^{\mathrm{ch}}(X) \in \BrMoncomp_{X,\alpha_X}$.

\emph{Step 4 (verify the object is well-defined).}
The conditional object requires three checks: compact generation of the
chosen chain model, conilpotence of the categorical bar coproduct, and
factorisation compatibility on $\Confbar(X)$. These checks are part of
the $H_{L2}$ package; \S~\ref{ssec:BCOV-transfer-X5} and
\S~\ref{ssec:explicit-bar-model} record the model calculations rather
than an all-CY$_3$ theorem.

\emph{Step 5 (paste to the explicit bar object).}
The $\infty$-functor $\Phi_3^{\mathrm{ch}}$ factors through the
explicit chain model
$B^{\mathrm{cat}}(D^b(X)) \in \BrMoncomp_{X,\alpha_X}$ after the
descent datum of Theorem~\ref{thm:pr-alpha-X-local-global} has been
chosen. The resulting diagram of $\infty$-functors
\begin{equation}
\label{eq:Phi-3-ch-commutative-platonic}
\begin{tikzcd}[column sep=large, row sep=large]
\mathrm{Perf}^{\mathrm{CY3}}_\infty(X)
 \arrow[r, "\Phi_3^{\mathrm{ch}}"]
 \arrow[d, "\mathrm{HKR}_\infty^{\mathrm{curv},\hbar}"']
&
\BrMoncomp_{X,\alpha_X}
 \arrow[d, "\mathrm{pr}_{\alpha_X}"]
\\
\mathrm{PV}^\bullet(X)[[\hbar]]
 \arrow[r, "B^{\mathrm{cat}}"']
&
\BrMoncomp_{X}
\end{tikzcd}
\end{equation}
commutes in the effective descent regime and otherwise commutes only
after the specified Cech-coherent descent homotopy. The upper path is
the L2 realisation of
Theorem~\ref{thm:grand-unification-platonic}; the lower path is the
chain-level realisation via BCOV and the explicit bar. The right
vertical $\mathrm{pr}_{\alpha_X}$ is the local gerbe-trivialising
projection after tensoring with a chosen local trivialisation of
$\alpha_X$. Francis-Gaitsgory universality \cite[Thm~6.3]{FG12}
together with Lurie \cite[HA~5.5.2.9]{LurieDAGX} supplies the
comparison once this descent datum is part of $H_{L2}$; it does not
annihilate the gerbe obstruction.

Property~(i) follows from Step~5. Property~(ii) is Step~2 together
with the descent-scoped projection of
diagram~\eqref{eq:Phi-3-ch-commutative-platonic}. Property~(iii)
identifies $\mathrm{ChirHoch}^\bullet$ with the Costello-Li BCOV
ambient Hochschild complex only on the $H_H+H_{L2}$ comparison
surface, combining Theorem~\ref{thm:theorem-h-on-koszul-locus} with
the BCOV transfer datum of Step~3. On the scope of the theorem, the
non-Tannakian stratum of Corollary~\ref{cor:gu-L2-platonic} is
detected by non-trivial gerbe or non-formal chain data in the
conditional image of $\Phi_3^{\mathrm{ch}}$.
\end{proof}

The two supporting inscriptions referenced in the proof are
recorded in the next subsections.

\subsection{Chain-level BCOV transfer on $X_5$}
\label{ssec:BCOV-transfer-X5}

The curved-$L_\infty$ quasi-isomorphism
$\mathrm{HKR}_\infty^{\mathrm{curv},\hbar}$ of \cite{CL20}
transfers the Dolbeault-BCOV action functional on
$\mathrm{PV}^\bullet(X_5)[[\hbar]]$ to the chain-level
$\infty$-operadic structure on
$\mathrm{Perf}^{\mathrm{CY3}}_\infty(X_5)$. The
Kodaira-Spencer $L_\infty$-algebra
$\mathrm{KS}(X_5) = (\mathrm{PV}^\bullet(X_5), \bar\partial, \{-,-\}_{\mathrm{SN}})$
admits a curved extension at every genus $g \leq g_{\max}(X_5)$
within the Costello-Li gauge; the induced $\infty$-structure on
$\mathrm{Perf}^{\mathrm{CY3}}_\infty(X_5)$ is the data passed to
Step~3 of the proof. Extension to arbitrary compact CY$_3$ is the
scope condition of
Theorem~\ref{thm:L2-chain-level-gerbe-platonic}.

\subsection{Explicit $B^{\mathrm{cat}}(D^b(X_5))$}
\label{ssec:explicit-bar-model}

Given the transfer datum of \S~\ref{ssec:BCOV-transfer-X5}, the bar
construction $B^{\mathrm{cat}}(D^b(X_5))$ is the explicit
chain-level coalgebra whose generators are the perfect complexes on
$X_5$ modulo quasi-isomorphism, whose coproduct is the
Fulton-MacPherson boundary of $\Confbar(X_5)$, and whose compatibility
with the Costello-Li BCOV structure is part of that datum. The
associator is twisted by $\alpha_{X_5}$; after the conilpotence and
factorisation checks included in $H_{L2}$,
$B^{\mathrm{cat}}(D^b(X_5))$ lies in
$\BrMoncomp_{X_5, \alpha_{X_5}}$.

Theorem~\ref{thm:L2-chain-level-gerbe-platonic} scopes the earlier
conditional formulation: the non-Tannakian surface is a chain-level
recognition statement on the subcategory of compact CY$_3$ targets
where the Costello-Li BCOV transfer and gerbe descent data are
supplied, with the gerbe twist retained in the target category.

\subsection{Local-global gluing of the gerbe-trivialising projection}
\label{ssec:pr-alpha-X-local-global}

The projection $\mathrm{pr}_{\alpha_X} : \BrMoncomp_{X,\alpha_X}
\to \BrMoncomp_X$ appearing in
diagram~\eqref{eq:Phi-3-ch-commutative-platonic} is defined
locally: on an open cover $\{U_i\}$ of $X$ over which
$\alpha_X|_{U_i}$ trivialises, tensoring with a local
trivialisation $\tau_i : \alpha_X|_{U_i} \xrightarrow{\sim} 0$
produces a gerbe-trivialised restriction
$\BrMoncomp_{U_i, \alpha_X|_{U_i}} \xrightarrow{\sim}
\BrMoncomp_{U_i}$. On overlaps $U_i \cap U_j$, the two local
trivialisations differ by a $\mathbb{C}^\times$-gerbe cocycle
$g_{ij} \in Z^1(U_i \cap U_j, \underline{\mathbb{C}^\times})$
whose cohomology class $[\{g_{ij}\}] \in \check H^3(X,
\underline{\mathbb{C}^\times})$ is $\alpha_X$ itself. The
question is whether the locally defined functors glue to an
honest $\infty$-functor on $X$, or only up to Čech-coherent
homotopy with obstruction in the Postnikov tower.

\begin{theorem}[Conditional local-global gluing of $\mathrm{pr}_{\alpha_X}$]
\label{thm:pr-alpha-X-local-global}
\ClaimStatusConditional
Let $X$ be a smooth projective variety and
$\alpha_X \in H^3(X, \underline{\mathbb{C}^\times})$ the gerbe
class under consideration. Fix a hypercover $U_\bullet\to X$ on which
$\alpha_X$ is trivialised. The local functors
$\mathrm{pr}_{\alpha_X|_{U_n}}$ glue as follows.
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Effective descent regime.} If a finite \'{e}tale Galois
cover $\pi:\widetilde X\to X$ is given, $\pi^*\alpha_X=0$, and the
resulting descent datum in
$\mathrm{Fun}_\infty(\BrMoncomp_{\widetilde X},
\BrMoncomp_{\widetilde X})$ is effective, then
$\mathrm{pr}_{\alpha_X}$ exists as an honest global
$\infty$-functor
\[
 \BrMoncomp_{X,\alpha_X}\longrightarrow \BrMoncomp_X .
\]
\item \emph{Hypercover regime.} Without such an effective descent
datum, the local projections determine only an object of the
totalisation
\[
 \mathrm{Tot}\,
 \mathrm{Fun}_\infty(\BrMoncomp_{U_\bullet,\alpha_X},
                    \BrMoncomp_{U_\bullet}).
\]
The obstruction to strict globalisation is the class of this
totalisation point in the descent Postnikov tower. It vanishes exactly
when the local projections are equivalent to a global
$\infty$-functor on $X$.
\end{enumerate}
Consequently, diagram~\eqref{eq:Phi-3-ch-commutative-platonic}
commutes strictly only in the effective descent regime. In the
hypercover regime it commutes only after choosing the indicated
descent homotopy, and the obstruction class is part of the L2 data.
\end{theorem}

\begin{proof}
\emph{Regime (a).} On $\widetilde X$ the class $\pi^*\alpha_X$
vanishes, so the twisted and untwisted targets are identified by the
chosen trivialisation. Effectivity of the Galois descent datum is
precisely the hypothesis that this local functor descends along the
\v Cech nerve of $\pi$. Giraud descent for gerbes
\cite[III.3.3.2]{Giraud1971} and Lurie descent for presentable
$\infty$-categories \cite[HA~1.3.1.7]{LurieDAGX} then give the global
functor.

\emph{Regime (b).} For an arbitrary hypercover, the local projections
form a cosimplicial diagram of $\infty$-functors. Joyal--Lurie descent
\cite[HTT~6.5.3.12]{LurieHTT} identifies global functors with the
descent-effective points of its totalisation. The Postnikov tower of
this totalisation records the successive homotopy-coherence
obstructions. Thus strict globalisation is equivalent to vanishing of
that obstruction tower. The commutativity of
diagram~\eqref{eq:Phi-3-ch-commutative-platonic} is therefore a
chosen descent homotopy, not an automatic consequence of the
bar--cobar adjunction.
\end{proof}

\begin{remark}[Strict compact CY$_3$ and the quintic]
\label{rem:pr-alpha-X-quintic}
If the Vol~III CY-side construction supplies, on the quintic
$X_5 \subset \mathbb{P}^4$, a gerbe class
$\alpha_{X_5} = [5 \cdot \mathrm{vol}] \in J^3(X_5) \subset
H^3(X_5, \underline{\mathbb{C}^\times})$ lies entirely in the
continuous Griffiths part
(Proposition~\ref{V3-prop:cy-c-beyond-joyce-three-CY3}(i) of
Vol~III, \texttt{cy\_c\_beyond\_k3e\_existence\_obstruction.tex})
and has infinite order, then Regime~(b) of
Theorem~\ref{thm:pr-alpha-X-local-global} applies:
$\mathrm{pr}_{\alpha_{X_5}}$ exists only up to Čech-coherent
homotopy, and diagram~\eqref{eq:Phi-3-ch-commutative-platonic}
commutes only after the chosen descent homotopy unless the obstruction
tower vanishes. Regime~(a) applies to polarised K3 surfaces only after
one supplies an effective finite descent datum for
$\alpha_{K3}^{\mathrm{tors}} \in
\mathrm{Br}(K3)$ and the Caldararu--Azumaya gerbe; the two regimes
separate the two descent problems in the Joyce--Brauer dictionary
(Remark~\ref{V3-rem:cy-c-beyond-quintic-joyce-not-brauer} of
Vol~III).
\end{remark}

\begin{conjecture}[Universal envelope as ambient]
\label{conj:universal-envelope-ambient-platonic}
\ClaimStatusConjectured
The universal envelope $\Uch_\cA = \cA \bowtie \cA^!_\infty$ is
the final object in the $\infty$-category of factorisation
$\infty$-bialgebras on $X$ which pair $\cA$ with a
factorisation-compatible Koszul-dual companion; equivalently,
every such pairing factors through $\Uch_\cA$.
\end{conjecture}

\begin{conjecture}[Genus-$g$ universality]
\label{conj:genus-g-universality-platonic}
\ClaimStatusConjectured
For every $g \geq 2$ and every class-M chiral algebra $\cA$, the
genus-$g$ trace $\trgenus(\Uch_\cA)$ admits a uniform-weight
decomposition whose cross-modular correction
$\delta F_g^{\mathrm{cross}}$ is a sum of
Fulton-MacPherson boundary contributions; equivalently, on
class~M the shadow-tower depth $r_{\max} = \infty$ forces a
non-trivial FM boundary contribution at every $g \geq 2$.
\end{conjecture}

\section{Reader's concordance: the unification map}
\label{sec:grand-theorem-concordance}

\begin{table}[h]
\centering
\begin{tabular}{l|l|l}
\hline
\textbf{Grand Theorem property} & \textbf{Classical theorem} & \textbf{Location} \\
\hline
(i) Universal twisting morphism & Theorem~A (bar--cobar) & Ch.~\ref{chap:bar-cobar} \\
(ii) Koszul duality locus & Koszul-locus discipline & Ch.~\ref{chap:koszul-pair-structure} \\
(iii) Positselski inversion & Theorem~B (coderived) & Ch.~\ref{ch:theorem-B-scope-platonic} \\
(iv) Derived-centre complementarity & Theorem~C ($\kappa + \kappa^!$) & Ch.~\ref{ch:theorem-C-refinements-platonic} \\
(v) Obstruction-tower universality & Theorem~D ($\mathrm{obs}_g(\cA)=\kappa(\cA)\lambda_g$) & Ch.~\ref{ch:higher-genus} \\
(vi) Hochschild concentration & Theorem~H on the Koszul/generic surface & Thm.~\ref{thm:theorem-h-on-koszul-locus} \\
(vii.L1) Chain-level ensemble & chain-level $\Theta_\cA$ & Ch.~\ref{ch:holographic-datum-master} \\
(vii.L2) Non-Tannakian categorical & non-formal / $\RW_d$-valued & Vol~III, \texttt{cy\_to\_chiral.tex} \\
(vii.L3) Presentable $\infty$-adjunction & Francis-Gaitsgory machinery & \cite[\S6]{FG11}, \cite[HA~5.2]{LurieDAGX} \\
\hline
\end{tabular}
\caption{The unification map: seven properties of the Grand
Theorem, their classical-theorem shadows, and their locations in
the manuscript.}
\label{tab:gu-unification-map-platonic}
\end{table}

The Grand Theorem
\ref{thm:grand-unification-platonic} records the structural arc of
Volume~I as a typed assembly diagram: the bar--cobar adjunction is the
spine, and every scalar, categorical, physical, or Calabi--Yau
projection enters only through its named comparison package.
