\chapter{Holographic codes from Koszul duality}
\label{chap:holographic-codes-koszul}
\index{holographic code!from Koszul duality|textbf}
\index{bar-cobar recovery!Koszul duality|textbf}

\providecommand{\KL}{\mathrm{KL}}
\providecommand{\QEC}{\mathrm{QEC}}

The five Beilinson-tower objects of the open quadrant are kept
separate throughout. Fix a chart $b$ in a factorisation dg-category
$\mathcal C^{\mathrm{op}}$ on $(X,D,\tau)$ and write
\[
\cA = A_b = \End_\mathcal{C}(b)\quad\text{(level 1, chart algebra),}
\qquad
B(\cA) = T^c(s^{-1}\bar\cA)\quad\text{(level 2, bar/twisting coalgebra),}
\]
\[
\cA^{\mathrm i} = H^\bullet B(\cA)\quad\text{(cohomology coalgebra),}
\qquad
\cA^! = ((\cA^{\mathrm i})^\vee)\quad\text{(Verdier dual algebra),}
\qquad
Z^{\mathrm{der}}_{\mathrm{ch}}(\cA) = C^\bullet_{\mathrm{ch}}(\cA,\cA)
\quad\text{(level 3, universal closed sector).}
\]
The bar coalgebra $B(\cA)$ is the twisting coalgebra at level~$2$;
the level-$3$ closed-sector object is the derived chiral centre
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$; the two never coincide. A
physical bulk enters only through a comparison map for a chosen
field theory. The bar-cobar adjunction
$\Omega^{\mathrm{ch}} \dashv B^{\mathrm{ch}}$
\textup{(}cobar left, bar right; Loday--Vallette 2012 Ch.~11,
Positselski 2011 Mem.\ AMS 996, Francis--Gaitsgory 2012
\emph{Selecta Math.} 18 Theorem~3.1\textup{)}
encodes the chart algebra into the bar/twisting coalgebra and recovers
the chart algebra through the bar-cobar counit. Theorem~B
\textup{(}bar-cobar inversion\textup{)} gives this algebraic recovery
on the Koszul locus:
$\Omega^{\mathrm{ch}}(B^{\mathrm{ch}}(\cA)) \xrightarrow{\sim} \cA$.
This inversion is not the construction of the Verdier dual algebra
$\cA^!$: the bar produces the cohomology coalgebra
$\cA^{\mathrm i}=H^\bullet B(\cA)$ first, and $\cA^!$ appears only
after Verdier duality on the finite-type or completed Koszul surface.
The level-$3$ closed sector is the derived chiral centre
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA) = C^\bullet_{\mathrm{ch}}(\cA,\cA)$,
identified with chiral Hochschild cochains by the open/closed theorem
of Chapter~\ref{ch:holographic-datum-master} and
Theorem~\ref{thm:thqg-swiss-cheese}; the bar coalgebra $B(\cA)$ is
not this object and is not the BRST observable algebra of any
physical theory. Four typed arrows are kept separate throughout this
chapter:
the bar-cobar counit
$\psi_\cA\colon\Omega_X^{\mathrm{cont}}(C_\cA)\to\cA$,
where $C_\cA$ is the raw or completed bar coalgebra at level~$2$;
the induced chiral Hochschild transport on
$C^\bullet_{\mathrm{ch}}(-,-)$; the universal open/closed action of
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA) = C^\bullet_{\mathrm{ch}}(\cA,\cA)$
on the boundary; and, for a chosen
holomorphic-topological theory~$T$, the physical comparison
$\beta_T$ from boundary-local BRST bulk observables to
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$.  The map $\beta_T$ is extra
physical realization data; it is not the bar-cobar counit and is not
induced by the counit alone.
Chapter~\ref{chap:entanglement-modular-koszul} derived
entanglement entropy from the scalar projection of this structure.
The full algebraic content is sharper:

\begin{center}
\fbox{\parbox{0.85\textwidth}{\centering
\textbf{Chiral Koszulness is equivalent to the bar-cobar counit
quasi-isomorphism: exact recovery of the level-$1$ chart algebra
from the level-$2$ bar/twisting coalgebra.} The Verdier-Lagrangian
structure supplies a linearized symplectic algebraic code skeleton; a
Hilbert-space quantum error-correcting code requires additional
unitary and analytic completion data; and a physical bulk requires
the level-$3$ derived chiral centre $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$
together with a $\beta_T$-comparison.
}}
\end{center}

\noindent
The characterizations of Koszulness (K1--K12,
Theorem~\ref{thm:koszul-equivalences-meta}: seven intrinsic
bidirectional equivalences, one listed consequence
(Barr--Beck--Lurie monadicity), one conditional
factorization-homology comparison, one one-way chiral Hochschild
consequence, one conditional on perfectness, and one one-directional
$\mathcal D$-module purity implication) yield corresponding conditions for the
bar-cobar counit to be a quasi-isomorphism.
The shadow depth classifies the non-scalar layers in the formal
MC obstruction tower.
The Lagrangian isotropy of Theorem~C provides the code/complement
decomposition as a symplectic \textup{(}not orthogonal\textup{)}
splitting.  Physical holographic reconstruction enters only after
one supplies the derived-centre/BRST comparison and the corresponding
Hilbert-space inner product.

% ======================================================================
%
% 1. SYMPLECTIC CODE STRUCTURE FROM LAGRANGIAN ISOTROPY
%
% ======================================================================

\section{Symplectic code structure from Lagrangian isotropy}
\label{sec:hc-knill-laflamme}
\index{symplectic code!from Lagrangian isotropy|textbf}

\begin{remark}[Two algebraic code structures]
\label{rem:hc-two-codes}
\index{holographic code!two structures}
The algebraic framework produces two distinct but related
code structures:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The \emph{linearized symplectic code}: $\cC = \mathbf{Q}_g(\cA) \subset
 \mathbf{C}_g(\cA) = \cH$
 (Lagrangian summand inside the ambient complex).
 This is the algebraic structure relevant to a Knill--Laflamme
 comparison after a physical inner product is supplied.
\item The \emph{functor code}: the bar functor sends the chart
 algebra $\cA$ at level~$1$ to the bar/twisting coalgebra $B(\cA)$
 at level~$2$, and decoding is the counit
 $\epsilon_\cA\colon\Omega(B(\cA))\to\cA$. Exact recovery means
 $\epsilon_\cA$ is a quasi-isomorphism on the Koszul locus.
 This is the structure relevant for bar-cobar reconstruction of the
 chart algebra; it is the level-$1$ to level-$2$ reflection,
 not the construction of the level-$3$ bulk
 $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$.
\end{enumerate}
The two are related: the linearized symplectic code governs the
genus-by-genus phase-space polarization, while the functor
code governs the full algebraic reconstruction.  Koszulness
condition~(K4) is exactly the bar-cobar counit quasi-isomorphism.
The Lagrangian splitting in~(a) is the conditional Theorem~C
upgrade, not a formal consequence of K4 alone.
\end{remark}

\begin{proposition}[Verdier isotropy and the Knill--Laflamme obstruction;
\ClaimStatusConditional]
\label{prop:hc-knill-laflamme}
\index{Knill--Laflamme condition|textbf}
\index{Lagrangian isotropy!Knill--Laflamme}
\textit{Type signature.} Quadrant: Open. Presentation: chain-level.
Level: $5$ (scalar genus-$g$ pairing on the conformal-block carrier).
Hypothesis package: chirally Koszul pair $(\cA, \cA^!)$;
finite-dimensional shadow window; Verdier involution $\sigma$ as in
Proposition~\textup{\ref{prop:lagrangian-eigenspaces}}; complementary
Lagrangian polarisation of Theorem~C.
\smallskip\noindent
Let $(\cA, \cA^!)$ be a chirally Koszul pair satisfying the
hypotheses of the Lagrangian clause of
Theorem~\textup{\ref{thm:quantum-complementarity-main}} at genus
$g\geq1$, with the Verdier/Shapovalov comparison of
Proposition~\textup{\ref{prop:lagrangian-eigenspaces}}.
Define:
\begin{itemize}
\item $\cH := \mathbf{C}_g(\cA)$ \quad
 \textup{(}ambient complex\textup{)},
\item $\cC := \mathbf{Q}_g(\cA)$ \quad
 \textup{(}Lagrangian summand, the linearized code subspace\textup{)},
\item $\mathcal E := \mathbf{Q}_g(\cA^!)$ \quad
 \textup{(}complementary Lagrangian; not an orthogonal complement
 unless a physical Hermitian form supplies one\textup{)}.
\end{itemize}
Conditional on the Lagrangian-eigenspace package in
Proposition~\textup{\ref{prop:lagrangian-eigenspaces}}, the following
two-layer symplectic structure holds:

\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Verdier isotropy \textup{(}summand decoupling\textup{)}.}
 The Verdier pairing $\langle \cdot, \cdot \rangle_{\mathbb{D}}$
 vanishes on $\cC \times \cC$ and on
 $\mathcal E \times \mathcal E$:
 \begin{equation}\label{eq:hc-verdier-isotropy}
 \langle v, w \rangle_{\mathbb{D}} = 0
 \quad\text{for } v, w \in \cC
 \;\;\text{(resp.\ both in } \mathcal E\text{)}.
 \end{equation}
 This is a Verdier-isotropic condition on each summand.  It is not
 the Hilbert-space Knill--Laflamme equation; it is the algebraic
 null-pairing that a symplectic code model must preserve.

\item \emph{Shapovalov cross-pairing \textup{(}non-degenerate, not orthogonal\textup{)}.}
 Define $\langle v, w \rangle_S := \langle v, \sigma(w)
 \rangle_{\mathbb{D}}$.
 Since $\cC = V^+$ and $\mathcal E = V^-$ are the $\pm1$-eigenspaces
 of the Verdier involution~$\sigma$
 \textup{(}Proposition~\textup{\ref{prop:lagrangian-eigenspaces}(iii)}\textup{)},
 the Shapovalov form restricts to:
 \begin{equation}\label{eq:hc-shapovalov-cross-pairing}
 \langle v, w \rangle_S = -\langle v, w \rangle_{\mathbb{D}}
 \quad\text{for } v \in \cC,\; w \in \mathcal E.
 \end{equation}
 In particular, $\cC$ and $\mathcal E$ are \emph{not}
 Shapovalov-orthogonal in general: the Verdier cross-pairing
 $\cC \times \mathcal E \to \bC$ is non-degenerate
 \textup{(}it is the Lagrangian polarization\textup{)},
 so the Shapovalov cross-pairing is equally non-degenerate
 with a sign flip.
 The bipartite decomposition
 $\cH = \cC \oplus \mathcal E$ is a \emph{Lagrangian}
 splitting \textup{(}Verdier-isotropic summands\textup{)},
 not an orthogonal one.
\end{enumerate}

\smallskip\noindent
Part~(i) establishes the \emph{Lagrangian prerequisite}
for the symplectic code: each summand is
self-orthogonal under the Verdier pairing,
so neither summand carries an internal Verdier pairing.
Part~(ii) shows the cross-pairing is non-degenerate
with a sign flip, giving a \emph{symplectic}
code/complement structure rather than an orthogonal one.
The full Knill--Laflamme condition
$P_\cC E_i^\dagger E_j P_\cC = \lambda_{ij} P_\cC$
for a physical error family $\{E_i\}$
requires, in addition, the physical Hilbert space inner product
\textup{(}from the state--operator correspondence
in unitary theories\textup{)}, which is a separate
structure from the Verdier pairing.
On a one-dimensional scalar conformal-block line the KL compression
condition is automatic; this one-channel fact does not identify the
whole genus-$1$ complementarity complex with a one-dimensional code.
\end{proposition}

\begin{proof}
\emph{Part (i).}
The Verdier involution $\sigma$ satisfies
$\langle \sigma(v), \sigma(w) \rangle_{\mathbb{D}} =
-\langle v, w \rangle_{\mathbb{D}}$
(anti-commutativity,
Proposition~\ref{prop:lagrangian-eigenspaces}(ii)).
For $v, w \in \cC = V^+$ (eigenvalue $+1$ of $\sigma$):
$\langle v, w \rangle_{\mathbb{D}} =
\langle \sigma(v), \sigma(w) \rangle_{\mathbb{D}} =
-\langle v, w \rangle_{\mathbb{D}}$,
so $\langle v, w \rangle_{\mathbb{D}} = 0$.
The same argument with eigenvalue $-1$ gives
isotropy of $\mathcal E$.

\emph{Part (ii).}
For $v \in \cC = V^+$ and $w \in \mathcal E = V^-$:
$\sigma(v) = v$ and $\sigma(w) = -w$, so
$\langle v, w \rangle_S = \langle v, \sigma(w)
\rangle_{\mathbb{D}} = \langle v, -w \rangle_{\mathbb{D}}
= -\langle v, w \rangle_{\mathbb{D}}$.
Since $V^+$ and $V^-$ are complementary Lagrangians,
the Verdier cross-pairing
$\langle -, - \rangle_{\mathbb{D}}\colon V^+ \times V^- \to \bC$
is a perfect pairing
\textup{(}non-degeneracy of the total form plus isotropy
of each factor\textup{)}.
Hence $\langle v, w \rangle_S = -\langle v, w \rangle_{\mathbb{D}}$
is equally non-degenerate.
\end{proof}

\begin{remark}[Relation to Almheiri--Dong--Harlow]
\label{rem:hc-adh-comparison}
\index{Almheiri--Dong--Harlow}
The Lagrangian decomposition
$\cH = \cC \oplus \mathcal E$
has the same bipartite form as the
Almheiri--Dong--Harlow \cite{Almheiri-Dong-Harlow15}
entanglement-wedge/complementary-wedge decomposition, but it is
only an algebraic model until a Hilbert-space completion and
subregion recovery maps are constructed.
The splitting is \emph{symplectic} (Verdier-isotropic
summands with non-degenerate cross-pairing,
\textup{(\ref{eq:hc-shapovalov-cross-pairing})}),
not orthogonal.
A class
$\Phi\in Z^{\mathrm{der}}_{\mathrm{ch}}(\cA) =
C^\bullet_{\mathrm{ch}}(\cA,\cA)$
in the level-$3$ derived chiral centre can be assigned to the
$\cC$-side only after the open/closed action and a support condition
for that action have been chosen.  Vanishing of the induced Verdier
pairing against $\mathcal E$ is an algebraic support condition.
Calling it an entanglement-wedge statement is a physical comparison
hypothesis, not a theorem of Verdier duality.
\end{remark}

\begin{theorem}[Symplectic code structure; \ClaimStatusConditional]
\label{thm:hc-symplectic-code}
\index{symplectic code|textbf}
\index{holographic code!symplectic structure|textbf}
\textit{Type signature.} Quadrant: Open. Presentation: chain-level.
Level: $5$ (scalar carrier $\mathbf{C}_g(\cA)$ as a
genus-$g$ symplectic vector space). Hypothesis package: chirally
Koszul pair $(\cA, \cA^!)$; perfectness/non-degeneracy of the
Verdier pairing; finite-dimensional Lagrangian window of Theorem~C
(reconstruction theorem: Theorem~C, level $5$, Lagrangian clause).
\smallskip\noindent
Let $(\cA, \cA^!)$ be a chirally Koszul pair satisfying the
hypotheses of the Lagrangian clause of
Theorem~\textup{\ref{thm:quantum-complementarity-main}}.
The Lagrangian decomposition
$\mathbf{C}_g(\cA) = \mathbf{Q}_g(\cA) \oplus \mathbf{Q}_g(\cA^!)$
defines a \emph{symplectic code} in the following precise sense:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Lagrangian code subspace.}
 The code subspace $\cC := \mathbf{Q}_g(\cA)$ is Lagrangian:
 it is Verdier-isotropic
 \textup{(}Proposition~\textup{\ref{prop:hc-knill-laflamme}(i)}\textup{)}
 and, in each finite-dimensional shadow window, half-dimensional:
 $\dim \cC = \tfrac{1}{2}\dim \mathbf{C}_g(\cA)$.

\item \emph{Symplectic projection.}
 The Lagrangian splitting determines
 the symplectic projection
 \[
 \pi_\cC \colon \mathbf{C}_g(\cA) \longrightarrow
 \mathbf{Q}_g(\cA)
 \]
 along $\mathbf{Q}_g(\cA^!)$.  For any algebraic operator $E$
 preserving the code summand \textup{(}i.e.,
 $E(\cC)\subset\cC$\textup{)}, one has
 $(\pi_\cC\circ E)|_\cC=E|_\cC$.  Thus projection removes the
 $\mathbf{Q}_g(\cA^!)$ component; it becomes a Knill--Laflamme
 recovery map
 only after a class of physical errors and a Hermitian inner product
 have been specified.

\item \emph{Non-degenerate cross-pairing.}
 The Verdier pairing restricted to
 $\cC \times \mathbf{Q}_g(\cA^!)$ is a perfect pairing
 with sign flip
 \textup{(}Proposition~\textup{\ref{prop:hc-knill-laflamme}(ii)}\textup{)},
 providing the non-degenerate duality between
 the code summand and its Lagrangian complement that replaces orthogonal
 complementarity in the symplectic setting.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(i) follows from Theorem~C:
$\mathbf{Q}_g(\cA) + \mathbf{Q}_g(\cA^!) = \mathbf{C}_g(\cA)$
with the summands complementary Lagrangians under the Verdier
pairing. Isotropy is
Proposition~\ref{prop:hc-knill-laflamme}(i);
half-dimensionality is the Lagrangian condition.

Part~(ii): given the direct sum decomposition
$\mathbf{C}_g(\cA) = \cC \oplus \mathcal E$ with
$\mathcal E = \mathbf{Q}_g(\cA^!)$, the projection
$\pi_\cC$ is well-defined. If $E(\cC) \subset \cC$,
then $E(v)\in\cC$ for $v\in\cC$, hence
$\pi_\cC(E(v))=E(v)$.  If additionally $E|_\cC=\id_\cC$,
the projection recovers the original code vector.  Without that
extra physical error model, the statement is a symplectic projection
statement rather than a full QEC recovery theorem.

Part~(iii) is Proposition~\ref{prop:hc-knill-laflamme}(ii):
the Verdier cross-pairing is non-degenerate by the
Lagrangian polarization, with the Shapovalov form
giving $\langle v, w \rangle_S = -\langle v, w
\rangle_{\mathbb{D}}$.
\end{proof}

\begin{proposition}[Symplectic projection is not Knill--Laflamme recovery;
\ClaimStatusProvedHere]
\label{prop:hc-projection-not-kl}
\index{Knill--Laflamme condition!projection obstruction}
\textit{Type signature.} Quadrant: Open. Presentation: chain-level
(symplectic vs.\ Hermitian). Level: $5$ (Hilbert-space completion of
the scalar carrier). Hypothesis package: Verdier symplectic splitting
of Theorem~C plus an external Hilbert completion
$H_{\mathrm{phys}}$ and physical error $*$-algebra $\mathfrak E$;
no further hypothesis is needed for the negative result.
\smallskip\noindent
Let $H_{\mathrm{phys}}$ be a Hilbert completion of
$\mathbf C_g(\cA)$ with orthogonal projection $P_\cC$ onto the
closure of $\cC$, and let $\mathfrak E$ be a physical error
$*$-algebra on $H_{\mathrm{phys}}$.  The Verdier splitting supplies
only the algebraic projection
$\pi_\cC\colon \cC\oplus\mathcal E\to\cC$.  For
$E\in\mathfrak E$ and $v\in\cC$, write
\[
E(v)=E_{\cC}(v)+E_{\mathcal E}(v),
\qquad
E_{\cC}(v)\in\cC,\quad E_{\mathcal E}(v)\in\mathcal E.
\]
Then $\pi_\cC E(v)=E_{\cC}(v)$.  Thus the symplectic projection
removes leakage into $\mathcal E$ but does not correct the logical
action $E_{\cC}$ on~$\cC$.  A Knill--Laflamme code for
$\mathfrak E$ is the additional Hilbert-space assertion
\[
P_\cC E_i^\dagger E_j P_\cC=\lambda_{ij}P_\cC
\qquad(E_i,E_j\in\mathfrak E),
\]
and it is not implied by Verdier isotropy.
\end{proposition}

\begin{proof}
The first assertion is the definition of projection along the direct
sum $\cC\oplus\mathcal E$.  It kills the second component and leaves
the first component unchanged.  The Knill--Laflamme equation is a
statement about the Hermitian adjoint in $H_{\mathrm{phys}}$ and the
compression of products $E_i^\dagger E_j$ to the code subspace.  The
Verdier form is bilinear, shifted, and anti-symplectic under~$\sigma$;
it neither defines the Hermitian adjoint nor forces the compression
above to be scalar.  A finite-dimensional countermodel makes the
failure visible: take
$V=\mathbb C e_1\oplus\mathbb C e_2\oplus
\mathbb C f_1\oplus\mathbb C f_2$ with
$\cC=\langle e_1,e_2\rangle$,
$\mathcal E=\langle f_1,f_2\rangle$, Verdier pairing
$\langle e_i,f_j\rangle_{\mathbb D}=\delta_{ij}$ and zero on
each summand, and the standard Hermitian form.  The operator
$E(e_1)=e_1$, $E(e_2)=2e_2$, $E(f_i)=0$ preserves~$\cC$ and creates
no leakage, but
$P_\cC E^\dagger E P_\cC=\operatorname{diag}(1,4)$ on~$\cC$, not a
scalar multiple of~$P_\cC$.  Hence the implication fails without the
stated physical data.
\end{proof}

\begin{remark}[Unitary Koszul algebras and physical QEC]
\label{rem:hc-unitary-physical-qec}
\index{Knill--Laflamme condition!unitary case}
\index{Tomita--Takesaki!modular conjugation}
For \emph{unitary} Koszul algebras
\textup{(}positive-definite Shapovalov form, physical
state--operator correspondence\textup{)},
the physical inner product provides a Hermitian
structure $\langle -, - \rangle_{\mathrm{phys}}$
on $\mathbf{C}_g(\cA)$ in addition to the Verdier
pairing. The question of whether
$\mathbf{Q}_g(\cA)$ and $\mathbf{Q}_g(\cA^!)$ are
\emph{orthogonal} in this physical inner product
is extra analytic data.  The Tomita--Takesaki analogy should be read
through a chosen real form: a modular conjugation is anti-linear,
whereas the Verdier involution used in Theorem~C is a complex-linear
cochain involution.  Compatibility means that the anti-linear modular
operator implements the same polarization after complexification, not
that Verdier isotropy itself is Hilbert-space orthogonality.
On a one-dimensional scalar conformal-block line the KL compression is
tautological; higher-dimensional conformal-block spaces require the
full error-algebra condition of Proposition~\ref{prop:hc-projection-not-kl}.
\end{remark}

\begin{conjecture}[Physical QEC at higher genus;
\ClaimStatusConjectured]
\label{conj:hc-physical-qec}
\index{Knill--Laflamme condition!higher genus conjecture}
\textit{Type signature.} Quadrant: Open. Presentation: Hilbert-space
chain-level. Level: $5$ (genus-$g$ scalar Hilbert completion).
Hypothesis package: unitary chirally Koszul pair $(\cA,\cA^!)$;
fixed Hilbert completion $H_{\mathrm{phys}}(\cA,g)$ of $\mathbf
C_g(\cA)$; physical error $*$-algebra $\mathfrak E_g$; expected
implementation by a Tomita--Takesaki modular conjugation.
\smallskip\noindent
Let $(\cA,\cA^!)$ be a unitary chirally Koszul pair and let
$g\geq1$.  Suppose a physical Hilbert completion
$H_{\mathrm{phys}}(\cA,g)$ of $\mathbf C_g(\cA)$ and a physical
error $*$-algebra $\mathfrak E_g$ are fixed.  The physical QEC
upgrade asserts:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the closures of $\mathbf Q_g(\cA)$ and
 $\mathbf Q_g(\cA^!)$ are orthogonal for
 $\langle-,-\rangle_{\mathrm{phys}}$;
\item for the orthogonal projection $P_\cC$ onto
 $\overline{\mathbf Q_g(\cA)}$,
 \[
 P_\cC E_i^\dagger E_j P_\cC
 =\lambda_{ij}P_\cC
 \qquad(E_i,E_j\in\mathfrak E_g).
 \]
\end{enumerate}
The Tomita--Takesaki expectation is that a compatible modular
conjugation supplies these two conditions in the unitary
holomorphic-topological theories arising from the open/closed
realization.  This remains a physical completion problem, not a
consequence of Theorem~C alone.
\end{conjecture}

% ======================================================================
%
% 2. BAR-COBAR RECOVERY AND DERIVED-CENTRE FUNCTORIALITY
%
% ======================================================================

\section{Bar-cobar recovery and derived-centre functoriality}
\label{sec:hc-koszulness-exact-qec}
\index{bar-cobar recovery!Koszul duality|textbf}

\begin{definition}[Typed recovery data]
\label{def:hc-typed-recovery-data}
For a complete augmented chiral algebra~$\cA$ in the ambient of
Theorem~\textup{\ref{thm:bar-cobar-inversion-qi}}, write
\[
C_\cA =
\begin{cases}
\bar B_X(\cA),&\text{in the raw finite-window lane},\\
\widehat{\bar B}_X(\cA),&\text{in the completed pro-conilpotent lane}.
\end{cases}
\]
The algebraic decoding map is the continuous bar-cobar counit
\[
\psi_\cA\colon\Omega_X^{\mathrm{cont}}(C_\cA)\longrightarrow\cA,
\qquad C_\cA\;\text{at level~}2,\quad
\cA\;\text{at level~}1.
\]
The intrinsic derived-centre transport is the restriction map
induced by $\psi_\cA$ on the level-$3$ derived chiral centre, in a
cofibrant resolved model:
\[
\psi_\cA^*\colon
Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)
= C^\bullet_{\mathrm{ch}}(\cA,\cA)
\longrightarrow
C^\bullet_{\mathrm{ch}}\bigl(
\Omega_X^{\mathrm{cont}}(C_\cA),
\Omega_X^{\mathrm{cont}}(C_\cA)\bigr)
= Z^{\mathrm{der}}_{\mathrm{ch}}\bigl(\Omega_X^{\mathrm{cont}}(C_\cA)\bigr).
\]
This map is internal to the chiral algebra category. For a
holomorphic-topological bulk theory~$T$ with boundary chart
algebra~$\cA$, the physical open/closed comparison is a continuous
brace dg algebra map of BRST cochain complexes
\[
\beta_T\colon
\bigl(\operatorname{Loc}_{\partial}
\operatorname{Obs}^{\mathrm{bulk}}(T), Q_{\mathrm{BRST}}\bigr)
\longrightarrow
Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)
= C^\bullet_{\mathrm{ch}}(\cA,\cA)
\]
as in
Proposition~\textup{\ref{prop:thqg-universal-action-not-reconstruction}}.
Physical reconstruction is the assertion that $\beta_T$ is a
quasi-isomorphism in the chosen analytic completion, together with
the relevant subregion recovery maps. The codomain is the level-$3$
bulk; the bar coalgebra $C_\cA$ at level~$2$ is the source of
$\psi_\cA$, not of $\beta_T$.
\end{definition}

\begin{proposition}[Theorem H is not a physical bulk-vanishing theorem;
\ClaimStatusProvedHere]
\label{prop:hc-theorem-h-scope}
\index{Theorem H!scope in holographic codes}
\index{chiral Hochschild cohomology!not physical bulk vanishing}
\textit{Type signature.} Quadrant: Open. Presentation: chain-level.
Level: $3$ (derived chiral centre
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA) = C^\bullet_{\mathrm{ch}}(\cA,\cA)$).
Hypothesis package: hypotheses of Theorem~H (finiteness + completion;
Class M needs completed/pro/$J$-adic ambient); the implication to
BRST-bulk amplitude requires the additional comparison
$\beta_T$ as quasi-isomorphism (no physical implication without
that hypothesis).
\smallskip\noindent
Under the hypotheses of Theorem~H, the statement
\[
H^n\bigl(\ChirHoch^\bullet(\cA,\cA)\bigr)=0
\qquad(n\notin\{0,1,2\})
\]
is a curve-level statement about the chiral Hochschild cochain complex
of the boundary chiral algebra~$\cA$ on~$X$.  It is not a vanishing
theorem for the BRST cohomology of an arbitrary
holomorphic-topological bulk theory~$T$, and it is not a statement
about topological or categorical Hochschild theories.  If the
physical comparison map $\beta_T$ of
Definition~\textup{\ref{def:hc-typed-recovery-data}} is a
quasi-isomorphism, then the boundary-local BRST complex in its source
inherits the same cohomological amplitude.  Without that hypothesis,
Theorem~H gives no physical bulk vanishing.
\end{proposition}

\begin{proof}
Theorem~H has input a chiral algebra~$\cA$ on a smooth curve and output
the cohomological amplitude of
$\ChirHoch^\bullet(\cA,\cA)$, computed from the curve and the
Fulton--MacPherson collision filtration.  The BRST observable complex
of a physical theory~$T$ has different input data: fields, a BRST
differential, and an analytic completion.  The only typed arrow between
these complexes in this chapter is $\beta_T$.  A quasi-isomorphism
preserves cohomological amplitude; absent such a quasi-isomorphism,
there is no functorial implication from the chiral Hochschild complex
to the physical BRST complex.
\end{proof}

\begin{theorem}[Koszulness, bar-cobar recovery, and derived-centre transport;
\ClaimStatusConditional]
\label{thm:hc-koszulness-exact-qec}
\index{G12|textbf}
\textit{Type signature.} Quadrant: Open. Presentation: chain-level.
Level: $1\leftrightarrow 2$ for clause~(i), $1\to 3$ for clause~(ii),
external level-$3$/level-$4$ comparison for clause~(iii). Hypothesis
package: complete augmented $\cA$ on a smooth projective curve $X$,
in either the raw finite-window or the completed pro-conilpotent
ambient of Theorem~\textup{\ref{thm:bar-cobar-inversion-qi}};
chiral-Koszul locus for clauses (i) and (ii); for clause (iii),
the additional Definition~\textup{\ref{def:hc-typed-recovery-data}}
comparison $\beta_T$ proved to be a quasi-isomorphism in the chosen
analytic completion. Reconstruction theorems invoked:
Theorem~A (level $1\!\leftrightarrow\!2$), Theorem~B
(level $1\!\to\!3$), Theorem~H concentration (level~$3$ amplitude),
Theorem~\ref{thm:thqg-swiss-cheese} open/closed identification of
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA) = C^\bullet_{\mathrm{ch}}(\cA,\cA)$.
\smallskip\noindent
Let $\cA$ be a complete augmented chiral algebra on a smooth
projective curve~$X$, in either the raw finite-window ambient or the
completed pro-conilpotent ambient of
Theorem~\textup{\ref{thm:bar-cobar-inversion-qi}}, and let
$\psi_\cA$ be the counit of
Definition~\textup{\ref{def:hc-typed-recovery-data}}.  Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\cA$ is chirally Koszul if and only if the bar-cobar counit
 $\psi_\cA\colon\Omega_X^{\mathrm{cont}}(C_\cA)\to\cA$
 is a quasi-isomorphism in the stated ambient.  This is condition
 K4 of Theorem~\textup{\ref{thm:koszul-equivalences-meta}} and the
 strict Koszul lane of Theorem~B.

\item On the Koszul locus, the level-$3$ derived chiral centre
 $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA) = C^\bullet_{\mathrm{ch}}(\cA,\cA)$
 is transported through this counit: chiral Hochschild cochains
 applied to $\psi_\cA$ give a quasi-isomorphism
 \[
 Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)
 = C^\bullet_{\mathrm{ch}}(\cA,\cA)
 \;\simeq\;
 C^\bullet_{\mathrm{ch}}\bigl(
 \Omega_X^{\mathrm{cont}}(C_\cA),
 \Omega_X^{\mathrm{cont}}(C_\cA)\bigr)
 = Z^{\mathrm{der}}_{\mathrm{ch}}(\Omega_X^{\mathrm{cont}}(C_\cA))
 \]
 in the cofibrant resolved model used for the curve-level
 Theorem~H. This is derived-centre transport between two Beilinson
 chart presentations of the same level-$3$ closed sector, not
 construction of a physical bulk theory: the bar coalgebra $C_\cA$ at level~$2$
 enters only as a domain for $\psi_\cA$, and the closed sector is the centre
 $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$, not $C_\cA$.

\item A physical holographic reconstruction theorem is obtained from
 \textup{(ii)} only after adding a comparison map $\beta_T$ for the
 chosen holomorphic-topological bulk theory and proving that $\beta_T$
 is a quasi-isomorphism of the completed BRST and chiral Hochschild
 cochain complexes.  The universal open/closed theorem supplies the
 target and universal action; it does not construct this comparison for
 an arbitrary physical theory.
\end{enumerate}
When $\cA$ is Koszul:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The Lagrangian decomposition
 $\cH_g = \cC \oplus \mathcal E$
 \textup{(}Theorem~C\textup{)}
 provides the linearized symplectic code/complement decomposition.

\item The Lagrangian code/complement decomposition holds with
 symplectic \textup{(}not orthogonal\textup{)} cross-pairing
 \textup{(}Proposition~\textup{\ref{prop:hc-knill-laflamme}}\textup{)}.
 The full Knill--Laflamme condition requires the physical inner
 product from the unitary state--operator correspondence.  On a
 one-dimensional genus-$1$ scalar line the KL compression is automatic;
 higher-dimensional conformal-block spaces still require the physical
 error model.

\item The shadow depth $r_{\max}(\cA)$ classifies the formal
 non-scalar shadow layers
 \textup{(}Theorem~\textup{\ref{thm:hc-shadow-redundancy}}\textup{)}.
 These layers are not Hilbert-space erasure distances until a physical
 error model and recovery map are supplied.

\item The entanglement entropy
 \textup{(}Theorem~\textup{\ref{thm:ent-scalar-entropy}},
 Chapter~\textup{\ref{chap:entanglement-modular-koszul}}\textup{)}
 is the scalar information functional attached to the modular
 characteristic.  It is not a formula for Hilbert-space code
 distance.
\end{enumerate}
\end{theorem}

\begin{proof}
(i):
Characterization~K4 of
Theorem~\ref{thm:koszul-equivalences-meta} states that
$\psi_\cA$ is a quasi-isomorphism if and only
if $\cA$ is Koszul.
Theorem~\ref{thm:bar-cobar-inversion-qi} supplies the precise ambient:
strict quasi-isomorphism on the Koszul lane and coderived comparison
off it under filtered pro-conilpotent hypotheses. The quasi-isomorphism
is exact algebraic recovery of the chart algebra at level~$1$ from
the bar/twisting coalgebra at level~$2$: the bar functor produces the
coalgebra $C_\cA$, and the counit $\psi_\cA$ decodes it on the Koszul
locus.

(ii):
In the cofibrant resolved chiral model, chiral Hochschild cochains
compute a derived endomorphism object and are invariant under
quasi-isomorphism of the algebra input. Restriction along $\psi_\cA$
therefore identifies the derived chiral centre
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA) = C^\bullet_{\mathrm{ch}}(\cA,\cA)$
with $Z^{\mathrm{der}}_{\mathrm{ch}}(\Omega_X^{\mathrm{cont}}(C_\cA))$.
The universal open/closed pair of Theorem~\ref{thm:thqg-swiss-cheese}
identifies this centre as the level-$3$ bulk; the bar coalgebra
$C_\cA$ at level~$2$ is the input to $\psi_\cA$ and is never the
bulk. Proposition~\ref{prop:hc-theorem-h-scope} supplies the scope
of the Theorem~H concentration used here.

(iii):
The step from the level-$3$ derived chiral centre
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA) = C^\bullet_{\mathrm{ch}}(\cA,\cA)$
to a physical AdS/HT bulk is the external comparison stated in the
holographic Hochschild conjecture: one must construct the physical
BRST observable algebra and prove that its boundary-local restriction
compares with the derived chiral centre by the map $\beta_T$ of
Definition~\ref{def:hc-typed-recovery-data}. The bar-cobar theorem
supplies the chart-algebra recovery (level $1\!\leftrightarrow\!2$)
and the derived-centre functoriality (level $1\!\to\!3$); it does
not identify an arbitrary physical bulk by itself.

Consequences (a)--(d) follow from the respective references:
(a)~Theorem~C,
(b)~Proposition~\ref{prop:hc-knill-laflamme},
(c)~Theorem~\ref{thm:hc-shadow-redundancy},
(d)~Theorem~\ref{thm:ent-scalar-entropy}.
\end{proof}

\begin{remark}[Non-Koszulness and failure of the canonical counit]
\label{rem:hc-non-koszul-failure}
\index{non-Koszul!code failure}
If $\cA$ is not Koszul, condition K4 fails in the strict lane:
the counit $\psi_\cA$ is not the quasi-isomorphism
asserted by Theorem~B.  Simple quotients
$L_k(\mathfrak g)$ at admissible or critical parameters are therefore
test cases, not automatic counterexamples: one must verify the
failure of the PBW collapse, the Shapovalov determinant input, and
the relevant completed ambient separately.  A physical information-loss
statement would require, in addition, the derived-centre/BRST
holographic comparison for that theory.
\end{remark}

% ======================================================================
%
% 3. SHADOW DEPTH AND FORMAL SLOTS
%
% ======================================================================

\section{Shadow depth as formal slot structure}
\label{sec:hc-redundancy}
\index{shadow depth!formal slot structure|textbf}
\index{shadow slots|textbf}

\begin{conjecture}[Shadow depth and filtered recovery models]
\ClaimStatusConjectured
\label{conj:thqg-shadow-depth-code-distance}
\index{shadow depth!filtered recovery models}
\textit{Type signature.} Quadrant: Open. Presentation: chain-level
(formal MC tower) plus external Hilbert error model. Level: $5$
(scalar shadow tower) lifted to physical recovery. Hypothesis
package: chirally Koszul $\cA$ in the standard-landscape scope;
fixed physical error model whose erasures match the non-scalar
shadow degrees.
\smallskip\noindent
Let a physical error model be supplied whose erasures are exactly the
non-scalar shadow degrees of the MC tower.  Then the formal number of
filtered recovery slots is
\[
\#\{\,r\ge 3:\Sh_r(\Theta_\cA)\neq 0\,\}.
\]
On a pure shadow-depth archetype this number is $r_{\max}(\cA)-2$
for finite $r_{\max}$ and countably infinite for class~$\mathbf M$.
The Hilbert-space code distance is not determined by shadow depth
alone; it depends on the physical inner product, the error algebra,
and the recovery maps.
\end{conjecture}

\begin{theorem}[Shadow depth controls the formal shadow slots;
\ClaimStatusConditional]
\label{thm:hc-shadow-redundancy}
\index{shadow depth!formal slots}
\textit{Type signature.} Quadrant: Open. Presentation: chain-level
(MC obstruction tower). Level: $5$ (scalar shadow algebra
$\cA^{\mathrm{sh}}_{r,\bullet}$) sourced from the level-$2$ bar
intrinsic MC element $D_\cA - \dzero$. Hypothesis package: chirally
Koszul $\cA$; standard-landscape scope of
Theorem~\textup{\ref{thm:shadow-archetype-classification}};
recursive existence theorem
(Theorem~\textup{\ref{thm:recursive-existence}}); shadow growth bound
(Theorem~\textup{\ref{thm:shadow-radius}}) for class~M convergence.
\smallskip\noindent
For a chirally Koszul algebra $\cA$ in the computed standard
landscape scope of
Theorem~\textup{\ref{thm:shadow-archetype-classification}}, the shadow
depth $r_{\max}(\cA)$ controls the non-scalar slots in the formal MC
obstruction tower as follows.

\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Fundamental datum.}
 The scalar-level shadow $\kappa(\cA)$
 \textup{(}degree~$2$\textup{)} is the first modular datum in the
 tower: it is the genus-$1$ scalar obstruction of Theorem~D.

\item \emph{Recursive lifting.}
 For each degree $r \ge 3$, the shadow
 $\Sh_r(\Theta_\cA) \in \cA^{\mathrm{sh}}_{r,\bullet}$
 \textup{(}as a cohomology class in the shadow algebra\textup{)}
 is the degree-$r$ projection of the canonical bar-intrinsic MC
 element $D_\cA-\dzero$.
 The recursive existence theorem
 \textup{(}Theorem~\textup{\ref{thm:recursive-existence}}\textup{)}
 gives a lift from degree $<r$ to degree~$r$ after the obstruction
 class in $H^2$ vanishes; choices of representative are controlled by
 the degree-$r$ $H^1$.  Thus a degree-$r$ shadow is a formal
 recovery slot only after a contraction, gauge convention, or
 physical recovery map has been fixed.

\item \emph{Slot count.}
 The number of non-scalar shadow slots on the pure archetype is:
 \begin{center}
 \renewcommand{\arraystretch}{1.3}
 \begin{tabular}{ccll}
 \textbf{Class} & $r_{\max}$ & \textbf{Non-scalar slots}
 & \textbf{Prototype} \\
 \midrule
 G & $2$ & $0$ & Heisenberg, lattice \\
 L & $3$ & $1$ & Affine Kac--Moody \\
 C & $4$ & $2$ & $\beta\gamma$ \\
 M & $\infty$ & $\aleph_0$ \textup{(}countably infinite\textup{)}
 & Virasoro, $W_N$
 \end{tabular}
 \end{center}
 For class~M with shadow radius $\rho(\cA) < 1$, the scalar shadow
 series converges absolutely.
\end{enumerate}
No Hilbert-space code-distance formula follows from these data.
The only universal degree statement is that the scalar tower begins
at degree~$2$.
\end{theorem}

\begin{proof}
\emph{Part (i).} The scalar shadow $\kappa(\cA)$ is the
genus-$1$ obstruction class (Theorem~D), determining the
modular curvature on the uniform-weight scalar lane. There is no
shadow degree below~$2$ in this tower.

\emph{Part (ii).} The recursive existence theorem
(Theorem~\ref{thm:recursive-existence}) constructs the
shadow obstruction tower $\Theta_\cA = \varprojlim \Theta_\cA^{\le r}$
by solving the MC equation at each degree. At degree $r \ge 3$,
the equation
$d(\Theta^{(r)}) + \tfrac{1}{2}\sum_{r_1+r_2=r}
[\Theta^{(r_1)}, \Theta^{(r_2)}] = 0$
determines the \emph{shadow class}
$[\Theta^{(r)}] \in H^0(\operatorname{gr}^r \fg^{\mathrm{mod}})$
from $\{\Theta^{(s)}\}_{s < r}$.
The representative $\Theta^{(r)}$ is determined only up to
the gauge freedom controlled by~$H^1$; $H^2$ controls the obstruction.
The bar-intrinsic representative $D_\cA-\dzero$ supplies the canonical
choice used in the monograph.  This is a formal lifting slot, not yet
a Hilbert-space recovery map.

\emph{Part (iii).}
Class~G: $\Sh_r = 0$ for $r \ge 3$; zero non-scalar slots.
Class~L: $\Sh_3 \ne 0$, $\Sh_r = 0$ for $r \ge 4$; one non-scalar slot.
Class~C: $\Sh_4 \ne 0$ (and possibly $\Sh_3$), $\Sh_r = 0$
for $r \ge 5$; two non-scalar slots.
Class~M: $\Sh_r \ne 0$ for all $r$; countably many non-scalar slots.
Convergence for class~M follows from the shadow growth rate
bound $|\Sh_r| = O(\rho(\cA)^r \cdot r^{-5/2})$
(Theorem~\ref{thm:shadow-radius}), with absolute convergence
for $\rho < 1$.
\end{proof}

% ======================================================================
%
% 4. THE 12-FOLD DICTIONARY
%
% ======================================================================

\section{The Koszulness--code dictionary}
\label{sec:hc-dictionary}
\index{Koszulness--code dictionary|textbf}

\begin{proposition}[Koszulness--code dictionary;
\ClaimStatusConditional]
\label{prop:hc-dictionary}
\index{Koszulness!code-theoretic meaning}
\textit{Type signature.} Quadrant: Open. Presentation: dictionary
(structural names for each Koszulness equivalence). Level: rows
range over $1\!\leftrightarrow\!2$ (K1--K6, K8--K10), $3$ (K7), and
$5$ (K11). Hypothesis package: K4, K8 unconditional on the Koszul
locus; K11 conditional on perfectness/non-degeneracy
(reconstruction theorem: Theorem~C); K12 one-directional (forward
only).
\smallskip\noindent
Each of the $12$ characterizations of chiral
Koszulness \textup{(}$8$ genuinely independent bidirectional
equivalences, $1$ Barr--Beck--Lurie restatement of the bar-cobar
counit quasi-isomorphism, $1$ one-way chiral Hochschild consequence,
$1$ perfectness-conditional Lagrangian criterion, $1$ one-directional
$\mathcal{D}$-module purity implication\textup{)}
\textup{(}Theorem~\textup{\ref{thm:koszul-equivalences-meta}}\textup{)}
admits an algebraic-code reading.  Entries marked ``exact'' are
mathematical identifications in this chapter.  Entries marked
``struct.'' are structural analogies: they name the algebraic
feature one would use in a physical code model, but they are not
Hilbert-space QEC theorems.

\begin{center}
\renewcommand{\arraystretch}{1.4}
\small
\begin{tabular}{l@{\;}l@{\;\;}l@{\;\;}c}
& \textbf{Koszulness condition}
& \textbf{Code property}
& \textbf{Status} \\
\midrule
K1 & PBW degeneration
 & graded systematic encoding
 & struct. \\
K2 & $A_\infty$ formality
 & minimal linear model
 & struct. \\
K3 & Ext diagonal vanishing
 & diagonal syndrome model
 & struct. \\
K4 & bar-cobar quasi-iso \textup{(}Thm~B\textup{)}
 & \textbf{exact boundary recovery}
 & exact \\
K5 & Barr--Beck--Lurie equivalence
 & categorical determinacy
 & struct. \\
K6 & FH concentrated in degree $0$
 & homological threshold
 & struct. \\
K7 & Theorem~H curve-level $\ChirHoch$ amplitude $[0,2]$
 & derived-centre amplitude
 & struct. \\
K8 & Kac--Shapovalov nonvanishing
 & non-degenerate Gram matrix
 & exact \\
K9 & FM boundary acyclicity
 & boundary locality
 & struct. \\
K10 & Shadow-formality (degrees 2,3,4)
 & shadow compatibility
 & struct. \\
K11 & Lagrangian criterion
 & half-dimensional Lagrangian subspace
 & exact* \\
K12 & Bifunctor decomposition
 & structured decoding
 & $\to$
\end{tabular}
\end{center}
exact* = exact after perfectness/nondegeneracy;\quad
$\to$ = one-directional \textup{(}forward proved\textup{)}.
\end{proposition}

\begin{proof}
The table is a dictionary, not an additional equivalence theorem.
The precise mathematical identifications are K4, K8, and K11
\textup{(}with K11 conditional on the perfect shifted-symplectic
package\textup{)}.  The remaining rows are structural names for
the algebraic inputs supplied by
Proposition~\ref{prop:thqg-barcobar-error-correction} and
Theorem~\ref{thm:koszul-equivalences-meta}.
The exact rows are as follows.

\emph{K4 (bar-cobar quasi-isomorphism).}
This is exactly Theorem~\ref{thm:hc-koszulness-exact-qec}(i):
the counit $\psi_\cA$ is a quasi-isomorphism precisely
on the Koszul locus in the stated ambient.

\emph{K8 (Kac--Shapovalov nonvanishing).}
Non-vanishing Kac--Shapovalov determinant means the code
Gram form is non-degenerate.  Vanishing at special levels is a
Gram degeneracy in the algebraic model; whether it is a physical
code failure depends on the Hilbert-space completion.

\emph{K11 (Lagrangian criterion).}
Under perfectness and non-degeneracy, Theorem~C gives
$\mathbf C_g(\cA)=\mathbf Q_g(\cA)\oplus\mathbf Q_g(\cA^!)$ with
both summands Lagrangian; in finite dimension this forces
$\dim\mathbf Q_g(\cA)=\frac12\dim\mathbf C_g(\cA)$.  This is a
Verdier-symplectic rate statement, not a Hilbert-space stabilizer
code theorem.

For the structural rows, the table records the algebraic datum that
would feed a code model: PBW associated gradeds for K1, formality for
K2, Ext diagonal concentration for K3, monadic comparison for K5,
factorization-homology concentration for K6, derived-centre
amplitude for K7, FM boundary acyclicity for K9, shadow-formality for
K10, and bifunctorial decomposition for K12.  K7 is the curve-level
Theorem~H statement of
Proposition~\ref{prop:hc-theorem-h-scope}; it is not a physical
bulk-vanishing theorem.  No extra QEC identity is asserted in those
rows.
\end{proof}

\begin{remark}[Algebraic parameters supplied by the model]
\label{rem:hc-universal-parameters}
\index{code rate!universal $1/2$}
\index{code distance!not determined by shadow depth}
The algebraic model supplies three parameters, each with its own
scope:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Verdier rate.}
 Under the finite-dimensional Lagrangian hypotheses of Theorem~C,
 $\dim \cC=\tfrac12\dim\cH$.
\item \emph{First degree.}
 The shadow tower begins at degree~$2$ with the scalar
 $\kappa(\cA)$.  This is not a Hilbert-space code-distance formula.
\item \emph{Formal shadow slots.}
 On a pure archetype, the number of non-scalar slots is
 $r_{\max}(\cA)-2$ for finite $r_{\max}$ and countably infinite for
 class~$\mathbf M$.
\end{enumerate}
The structure is symplectic in the Verdier sense.  A statement about
a stabilizer group requires a physical Hilbert-space
realization and an error algebra.
\end{remark}

% ======================================================================
%
% 5. STANDARD LANDSCAPE CODE CENSUS
%
% ======================================================================

\section{Code census for the standard landscape}
\label{sec:hc-census}
\index{standard landscape!code census|textbf}

\begin{theorem}[Standard landscape code census;
\ClaimStatusConditional]
\label{thm:hc-census}
\textit{Type signature.} Quadrant: Open. Presentation: chain-level.
Level: $1\!\leftrightarrow\!2$ (bar-cobar inversion) plus level-$5$
shadow-slot count. Hypothesis package: PBW/Koszul hypotheses on
each landscape row
(Proposition~\textup{\ref{prop:pbw-universality}}); shadow archetype
classification
(Theorem~\textup{\ref{thm:shadow-archetype-classification}});
shadow-slot tabulation
(Theorem~\textup{\ref{thm:hc-shadow-redundancy}}); for class M,
absolute convergence requires
$\rho(\cA) < 1$
(Theorem~\textup{\ref{thm:shadow-radius}}).
\smallskip\noindent
Each row of the computed standard-landscape surface satisfying the
PBW/Koszul hypotheses admits bar-cobar exact recovery of the chart
algebra.  The formal shadow slots and heuristic physical labels are:

\begin{center}
\renewcommand{\arraystretch}{1.3}
\small
\begin{tabular}{l@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}l}
\textbf{Family} & \textbf{Class} & \textbf{Slots}
& \textbf{Algebraic type} & \textbf{Heuristic physical label} \\
\midrule
Heisenberg $\mathcal{H}_\kappa$
 & G & $0$ & scalar & abelian CS \\
Lattice $V_\Lambda$
 & G & $0$ & scalar & lattice gauge \\
Affine $\widehat{\mathfrak{g}}_k$
 & L & $1$ & cubic & non-abelian CS \\
$\beta\gamma$
 & C & $2$ & quartic/contact & topological B-model \\
Virasoro $\mathrm{Vir}_c$
 & M & $\aleph_0$ & infinite shadow tower & 3d gravity \\
$W_N$
 & M & $\aleph_0$ & infinite shadow tower & higher-spin gravity
\end{tabular}
\end{center}
For class~M families, the scalar shadow series converges absolutely
when $\rho(\cA) < 1$
\textup{(}$c > c_\star \approx 6.125$ for Virasoro\textup{)}.
\end{theorem}

\begin{proof}
Koszulness of the freely strongly generated rows follows from the
PBW criterion
\textup{(}Proposition~\textup{\ref{prop:pbw-universality}}\textup{)}
and the family-specific verifications in
Part~\ref{part:characteristic-datum}.  The shadow slots follow from
the shadow archetype classification
(Theorem~\ref{thm:shadow-archetype-classification}) and
Theorem~\ref{thm:hc-shadow-redundancy}.
\end{proof}

\begin{remark}[Heuristic gravitational reading of the shadow slots]
\label{rem:hc-gravitational-code-complexity}
\index{gravitational complexity!code complexity}
The following physical reading is heuristic until the
derived-centre/BRST comparison and Hilbert-space recovery maps are
constructed:
\begin{itemize}
\item \emph{Scalar type} (G):
 The shadow tower has no non-scalar slot.  In the Gaussian
 gravitational reading, the scalar entropy has no shadow correction
 (Chapter~\ref{chap:entanglement-modular-koszul},
 Proposition~\ref{prop:ent-complexity-classification}).

\item \emph{Cubic type} (L):
 One non-scalar slot, the cubic shadow, is available.  In the
 tree-level reading this is the algebraic place where a three-point
 interaction can be compared with lower-degree data.

\item \emph{Contact type} (C):
 Two non-scalar slots, cubic and quartic, are available.
 The quartic contact invariant
 $\mathfrak{Q}^{\mathrm{contact}}$
 is the second formal shadow datum.

\item \emph{Infinite shadow type} (M):
 There is one formal slot at each degree.  The MC equation supplies
 the recursive algebraic constraint, while convergence for
 $\rho<1$ is convergence of the scalar shadow series, not by itself
 a physical error-correction theorem.
\end{itemize}
\end{remark}
