% ======================================================================
% OUTLOOK: compact mathematical boundary conditions for the monograph:
% the five theorem packages, the object firewall, and the exact
% proof-obligation carriers left by the proved and conditional surfaces.
% ======================================================================

\chapter{Outlook}
\label{chap:outlook}

\index{concordance|textbf}

\section{The five main theorems}
\label{sec:outlook-five-theorems}

The algebraic engine rests on five theorem packages. Each package is
read below at its proved or conditional surface; no cross-volume
statement is used as proof input for a Vol~I theorem.

\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{clp{7.5cm}l}
& \textbf{Theorem} & \textbf{Statement} & \textbf{Status} \\
\hline
\textbf{A} & Bar-cobar adjunction
 & Chain-level $\Omegach \dashv \barBch$ on $\Ran(X)$,
 with Verdier intertwining after $\mathbb D_{\Ran}$
 \textup{(}Thm~\ref{thm:bar-cobar-isomorphism-main}\textup{)}
 & \ClaimStatusProvedHere \\
\textbf{B} & Bar-cobar inversion
 & $\Omegach(\barBch(\cA)) \xrightarrow{\sim} \cA$ on the strict
 Koszul locus; off-locus continuation only in the filtered
 coderived/pro-conilpotent ambient
 \textup{(}Thm~\ref{thm:bar-cobar-inversion-qi}\textup{)}.
 The higher-genus component
 \textup{(}Thm~\ref{thm:higher-genus-inversion}\textup{)}
 is conditional on the stated modular Koszul axioms
 & strict/coderived lanes \ClaimStatusProvedHere; higher genus
 \ClaimStatusConditional \\
\textbf{C} & Complementarity
 & Homotopy eigenspace decomposition and Verdier Lagrangian pairing
 for $(\cA,\cA^!)$
 \textup{(}Thm~\ref{thm:quantum-complementarity-main}\textup{)};
 shifted-symplectic/BV upgrade only under perfectness and
 non-degeneracy
 & C0/C1 \ClaimStatusProvedHere; C2 \ClaimStatusConditional \\
\textbf{D} & Modular characteristic
 & $F_g(\cA)=\kappa(\cA)\lambda_g^{\mathrm{FP}}
 +\delta F_g^{\mathrm{cross}}(\cA)$; on the uniform-weight
 scalar lane,
 $\mathrm{obs}_g(\cA)=\kappa(\cA)\lambda_g$
 \textup{(}Thms~\ref{thm:modular-characteristic},
 \ref{thm:genus-universality}\textup{)}
 & scalar lane \ClaimStatusProvedHere; all-weight/cross-channel
 \ClaimStatusConditional \\
\textbf{H} & Chiral Hochschild
 & Chiral, not topological or categorical, Hochschild cohomology:
 amplitude $[0,2]$ for PBW Koszul inputs with
 $E_\infty$-chiral completion; symmetric $E_1$-only and
 non-generic class~M cases remain conjectural
 \textup{(}Thm~\ref{thm:main-koszul-hoch},
 Cor.~\ref{cor:hochschild-averaging-symmetric},
 Conjs.~\ref{conj:hochschild-concentration-E1-only},
 \ref{conj:hochschild-concentration-class-M-non-generic}\textup{)}
 & generic PBW surface \ClaimStatusProvedHere; exceptional surfaces
 \ClaimStatusConjectured
\end{tabular}
\end{center}

\noindent
The five objects remain distinct throughout:
\[
\cA,\qquad
\barB^{\mathrm{ch}}(\cA),\qquad
\cA^i := H^*(\barB^{\mathrm{ch}}(\cA)),\qquad
\cA^! := \mathbb D_X(\cA^i),\qquad
Z^{\mathrm{der}}_{\mathrm{ch}}(\cA).
\]
The counit $\Omegach\barBch(\cA)\to\cA$ is bar-cobar inversion.
It is not the definition of the Verdier-side Koszul dual~$\cA^!$,
and $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ is the chiral Hochschild
derived centre, not a bar coalgebra.

\smallskip\noindent
The modular $L_\infty$ convolution algebra
$\mathfrak{g}^{\mathrm{mod}}_\cA$ carries a natural modular $L_\infty$
structure from the Feynman transform of the modular operad. The dg~Lie
algebra of Definition~\ref{def:modular-convolution-dg-lie} is its strict
model $\Convstr$; the homotopy-invariant object is $\Definfmod(\cA)$
(Theorem~\ref{thm:modular-homotopy-convolution}). The universal MC element
$\Theta_\cA \in \MC(\gAmod)$ exists unconditionally by the bar-intrinsic
construction (Theorem~\ref{thm:mc2-bar-intrinsic}: $\Theta_\cA := D_\cA - d_0$
is MC because $D_\cA^2 = 0$). The shadow obstruction tower
$\Theta_\cA^{\le 2} \to \Theta_\cA^{\le 3} \to \Theta_\cA^{\le 4}
\to \cdots$ consists of its finite-order projections.
Theorems~A--C read the adjunction, inversion, and Verdier-centre
consequences of this MC package. Theorems~D and~H are respectively
the scalar modular characteristic and the chiral Hochschild shadow.

% ======================================================================

\section{Three inputs to the modular MC element}
\label{sec:outlook-three-pillars}
\index{modular MC element!three inputs|textbf}
\index{homotopy chiral algebra!foundational role}
\index{convolution!sL-infinity@$sL_\infty$-algebra!foundational role}
\index{logarithmic Fulton--MacPherson!foundational role}

The construction of~$\Theta_\cA$ uses three independent inputs.
They meet in the master MC equation
$D\cdot\Theta_\cA + \tfrac{1}{2}[\Theta_\cA,\Theta_\cA] = 0$.
The local input is a homotopy chiral algebra on the curve. The
deformation input is the filtered convolution $sL_\infty$-algebra
controlling twisting morphisms. The global input is logarithmic
Fulton--MacPherson collision geometry.

\begin{remark}[The three inputs]
\label{rem:three-pillars}
\index{three-pillar architecture!summary}
The primitive objects of the theory are:
\begin{enumerate}[label=\textup{(\Alph*)}]
\item \textbf{Local algebraic object}. The primitive local
 object is a \emph{homotopy chiral algebra}
 ($\mathrm{Ch}_\infty$-algebra) in the sense of
 Malikov--Schechtman~\cite{MS24}, not a strict chiral algebra. A strict
 chiral algebra appears only after rectification or on cohomology.
 The chain-level story is
 $\mathrm{Ch}_\infty \to \text{strict chiral algebra on } H^\bullet
 \to \text{PVA/Poisson shadow}$.

\item \textbf{Deformation-control object}. The universal
 deformation machine is a \emph{filtered convolution $sL_\infty$-algebra}
 $\operatorname{hom}_\alpha(\cC, \cA)$ relative to a twisting morphism
 $\alpha$, in the sense of Robert-Nicoud--Wierstra~\cite{RNW19} and
 Vallette~\cite{Val16}. The deformation space is the Maurer--Cartan
 $\infty$-groupoid $\mathrm{MC}_\bullet(\operatorname{hom}_\alpha)$.
 The dg~Lie algebra $\mathfrak{g}_\cA^{\mathrm{mod}}$ of
 Definition~\ref{def:modular-convolution-dg-lie} is the strict model of
 the homotopy-invariant $\Definfmod(\cA)$
 (Theorem~\ref{thm:modular-homotopy-convolution}).

\item \textbf{Global collision geometry}. The natural
 geometry for punctured curves, nodal degenerations, and modular sewing
 is \emph{logarithmic Fulton--MacPherson} compactification
 $\overline{\operatorname{FM}}_n(X|D)$ on simple normal crossings pairs
 $(X, D)$, in the sense of Mok~\cite{Mok25}. Ordinary FM
 compactification is the special case $D = \emptyset$. The
 tropicalization of $\overline{\operatorname{FM}}_n(X|D)$ is controlled
 by planted-forest combinatorics
 (Definition~\ref{def:planted-forest-coefficient-algebra}).
\end{enumerate}
\end{remark}

\begin{remark}[Compatibility of the three inputs]
\label{rem:three-pillar-triangle}
\index{three-pillar architecture!triangle}
The bar complex
$\barB(\cA)$ is simultaneously:
\begin{itemize}
\item a $\mathrm{Ch}_\infty$-algebra (via cosimplicial structure
 and the Eilenberg--Zilber operad $\mathcal{Y}(n)$);
\item an algebra in
 $\operatorname{hom}_\alpha(\cC^{\textup{!\textasciigrave}}_{\mathrm{ch}},
 \cP^{\mathrm{ch}})$ (via the chiral operadic twisting
 morphism);
\item a sheaf on $\overline{\operatorname{FM}}_n(C|D)$ for a curve~$C$
 with divisor~$D$ (via log-smooth compactification of
 operator insertions).
\end{itemize}
The pairwise compatibilities are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item A+B: the $\infty$-category of chiral algebras
 (\cite[Theorem~3.8]{Val16} gives simplicial structure; \cite{MS24}
 gives operations);
\item B+C: the geometric convolution algebra (planted forests of
 Mok~\cite{Mok25} are the combinatorial data controlling the
 convolution bracket on $\mathfrak{g}_\cA^{\mathrm{mod}}$);
\item A+C: the geometric origin of higher homotopies (secondary Borcherds
 operations $j'_{(p,q,r)}$ are residues on FM boundary strata; log-FM
 degeneration organizes these across genera).
\end{enumerate}
\end{remark}

\begin{remark}[Design constraint: failure of two-sided bifunctoriality]
\label{rem:no-bifunctor}
\index{bifunctoriality!failure of two-sided}
\index{one-slot obstruction}
Robert-Nicoud--Wierstra~\cite[Section~6]{RNW19} prove that although
the convolution functor $\operatorname{hom}_\alpha(-,-)$ extends to
$\infty_\alpha$-morphisms in either slot separately, there is
\emph{no} honest bifunctor accepting $\infty$-morphisms in both slots
simultaneously. The MC3 categorical lift must proceed one slot at a
time.
\end{remark}

% ======================================================================

\section{Core surfaces and nonlinear invariants}
\label{sec:three-rings}
\index{modular Koszul duality!core surfaces|textbf}

The proved core consists of the A/B/C/D/H packages at the scopes
stated in \S\ref{sec:outlook-five-theorems}, MC1--MC4, and the strict parts of
MC5 on the analytic/coderived, Mittag--Leffler pro-object,
$J$-adic, and filtered weight-completed surfaces. The bounded
direct-sum ambient $\mathrm{Ch}(\mathrm{Vect})$ is not a class~M
chain-level theorem: generic
$S_4(\mathrm{Vir}_c)=10/[c(5c+22)]$ detects the raw direct-sum
obstruction. The completed tower is the repair.

\smallskip\noindent
The shadow obstruction tower
$\Theta_\cA^{\leq r}$ is the finite-order projection tower of the
bar-intrinsic MC element
\textup{(}Theorem~\ref{thm:mc2-bar-intrinsic}\textup{)}. Its depth
classifies complexity, not Koszulness:
\[
\mathsf G:r_{\max}=2,\qquad
\mathsf L:r_{\max}=3,\qquad
\mathsf C:r_{\max}=4,\qquad
\mathsf M:r_{\max}=\infty .
\]
On a primary line the shadow metric~$Q_L$
\textup{(}Definition~\ref{def:shadow-metric}\textup{)} reduces the
tower to $(\kappa,\alpha,S_4)$. The relation
$H^2=t^4Q$ \textup{(}Theorem~\ref{thm:riccati-algebraicity}\textup{)}
makes the infinite class~M tower algebraic of degree~$2$, and the
logarithmic shadow connection has monodromy~$-1$ at the branch
points with curvature equal to the propagator variance
\textup{(}Theorem~\ref{thm:shadow-connection},
Proposition~\ref{prop:propagator-variance}\textup{)}.

\smallskip\noindent
The Yangian/RTT surface is proved only on the
evaluation-generated core for all simple types; the extension to the
full compact/completed Drinfeld--Kohno category is Conjecture
\ref{conj:dk-compacts-completion}. Holomorphic-topological and
Calabi--Yau realizations belong to the compatibility statements in
\S\ref{sec:cross-volume-bridges}.

% ======================================================================

\section{Factorization-envelope technology}
\label{sec:concordance-nishinaka-vicedo}
\index{Nishinaka|textbf}
\index{Vicedo|textbf}
\index{factorization envelope!Lie conformal|textbf}

The envelope-shadow functor
(\S\ref{subsubsec:envelope-shadow-functor}) upgrades the shadow
obstruction tower from an invariant of a fixed chiral algebra to a
functor on cyclically admissible Lie conformal input
(Definition~\ref{def:v1-cyclically-admissible}). The modular Koszul
datum $\Pi_X(L)$ (Construction~\ref{constr:v1-platonic-package})
organizes the resulting data into a modular package with six primary
entries: factorization envelope, bar coalgebra, universal MC class,
determinant line, spectral branch object, and quartic resonance class.
The bar entry is not the Koszul dual algebra. It first produces the
bar-dual coalgebra \(A^i=H^*(B(A))\); Verdier duality then gives
\(A^!\) only on the finite-type or completed Koszul surface. The
successive shadows descend from this typed package.

% ======================================================================

\section{Koszulness characterizations}
\label{sec:concordance-koszulness-theory}
\index{Koszulness!characterizations|textbf}

The meta-theorem (Theorem~\ref{thm:koszul-equivalences-meta}) lists
twelve tests for chiral Koszulness: seven intrinsic bidirectional
equivalences (items~(i)--(v), (ix)--(x)); item~(vi)
Barr--Beck--Lurie as a listed consequence of~(v); item~(vii) as a
conditional factorization-homology comparison, becoming a criterion
only under the detecting strengthening; item~(viii) chiral Hochschild
concentration and duality as a one-way consequence on the Koszul
locus; item~(xi) the Lagrangian
criterion, conditional on perfectness and non-degeneracy
(unconditional for the standard landscape); and item~(xii)
$\mathcal{D}$-module purity as a one-directional implication
((xii)$\Rightarrow$(x) proved; converse proved for affine
Kac--Moody at non-critical level, unproved for Virasoro and
$\mathcal{W}$).
Shadow depth $r_{\max}$ classifies the \emph{complexity} of Koszul
algebras ($\mathbf{G}/\mathbf{L}/\mathbf{C}/\mathbf{M}$ classes),
not Koszulness itself. The single-line dichotomy
(Theorem~\ref{thm:single-line-dichotomy}) proves that on any
one-dimensional primary slice, $r_{\max} \in \{2, 3, \infty\}$;
the contact class $\mathbf{C}$ ($r_{\max} = 4$) escapes via stratum
separation in $\Defcyc^{\mathrm{mod}}$.

\subsection{Operadic complexity theorem}
\label{subsec:concordance-operadic-complexity}
\index{operadic complexity|textbf}

\begin{theorem}[Operadic complexity; \ClaimStatusConditional]
\label{thm:operadic-complexity}
For a modular Koszul chiral algebra~$\cA$ satisfying the
shadow--formality comparison hypotheses of
Theorem~\ref{thm:operadic-complexity-detailed},
\[
r_{\max}(\cA)=d_\infty(\cA)=f_\infty(\cA),
\]
where $r_{\max}$ is the shadow termination degree, $d_\infty$
is the transferred $A_\infty$-depth, and $f_\infty$ is the
transferred genus-$0$ $L_\infty$-formality level.
\end{theorem}

% ======================================================================

\section{Proof boundaries}
\label{sec:modular-koszul-theory}
\index{proof boundaries|textbf}

These boundary assertions are not proof inputs for
Theorems~A/B/C/D/H. Each item names the carrier whose construction or
vanishing decides the boundary. MC1--MC4 are proved. MC5 is proved on the
analytic/coderived, strict Mittag--Leffler pro-object, $J$-adic
topological, and filtered weight-completed chain surfaces. The bounded
direct-sum ambient $\mathrm{Ch}(\mathrm{Vect})$ remains obstructed for
class~M, detected at generic $c$ by
$S_4(\mathrm{Vir}_c)=10/[c(5c+22)]\neq 0$. The tree-level amplitude
pairing remains conditional on perfectness and non-degeneracy.
MC3 is proved on the evaluation-generated core for all simple types by
Theorem~\ref{thm:categorical-cg-all-types} and
Corollary~\ref{cor:mc3-all-types}; the full
$\mathrm{DK}_g$ statement remains conditional on
Conjectures~\ref{conj:rank-independence-step2},
\ref{conj:mc3-automatic-generalization}, and
\ref{conj:dk-compacts-completion}. No theorem in this chapter covers
logarithmic $\cW(p)$, $N=2$ superconformal algebras, cosets,
non-rational lattice algebras, or roots of unity.

\begin{enumerate}[label=\textup{(\arabic*)}]
\item \emph{Non-principal $\mathcal W$-algebra duality beyond
 hook type.} Hook type in type~$A$ is proved by
 Theorem~\ref{thm:hook-type-transport-koszul-duality}. The first
 non-hook two-row case is the partition $(3,2)$ of
 $\mathfrak{sl}_5$. Its BRST nilradical
 $\mathfrak n_+$ is two-step of dimension~$8$ with
 $[\mathfrak n_+,\mathfrak n_+]\neq0$. The carrier is the
 transferred DS-bar differential; the decision criterion is existence
 of a chiral Koszul pair after replacing abelian nilradical formality
 by an explicit higher-BRST homotopy.
\item \emph{Relative Theorem~A over
 $\overline{\mathcal M}_{g,n}$.} The fixed-curve adjunction is
 Theorem~\ref{thm:bar-cobar-isomorphism-main}. The carrier is
 six-functor base change for the Ran prestack over
 $\overline{\mathcal M}_{g,n}$, including boundary divisors. The
 precise consequence is the genus-$g\geq2$ scalar lane of
 Theorem~D and clutching uniqueness for
 $\mathrm{obs}_g(\cA)/\kappa(\cA)=\lambda_g$.
\item \emph{Pronilpotent modular-graph closure.} The carrier is a
 pronilpotent modular convolution algebra in which the
 weight-completed $\Theta_\cA$ is the connected stable-graph
 exponential satisfying
 $d\Theta+\frac12[\Theta,\Theta]+\hbar\,\Delta\Theta=0$. The two
 chain-level inputs are
 $\mathrm{gr}_\rho\widehat B(\cA)\simeq\mathrm{Cum}_c(\cA)$
 and the jet principle for classes~$\mathsf C$ and~$\mathsf M$.
\item \emph{$\mathcal D$-module purity converse for Virasoro and
 $\mathcal W$-algebras.} The converse is proved for affine
 Kac--Moody by the Hitchin connection and its variation of Hodge
 structure on the KZ local system. For Virasoro and
 $\mathcal W$-algebras the carrier is the BPZ connection. The
 proof boundary is binary: construct a variation of Hodge structure
 on that connection, or identify the first failed VHS axiom; see
 Question~\ref{q:bpz-hitchin}.
\item \emph{Analytic sewing for interacting standard algebras.} For
 $\widehat{\mathfrak{sl}}_2$ at $k=1$, the algebraic
 Frenkel--Kac--Segal construction exists. The analytic carrier is a
 norm estimate for charge-shift vertex operators between Fock sectors.
 For the conformally flat disk, metric independence is
 proved for Heisenberg by Moriwaki's Bergman-space Fredholm
 determinant; the interacting case is decided by the same norm carrier.
\item \emph{Givental--Stokes extraction of
 $A_{\mathrm{cross}}(c)$.} The complementarity propagator~$P_\cA$ is
 the Givental $R$-matrix
 \textup{(}Theorem~\ref{thm:cohft-reconstruction}\textup{)}. The
 carrier is the Stokes matrix of the $A_2$ Frobenius CohFT
 three-branch-point spectral curve; its extraction determines the
 closed rational function $A_{\mathrm{cross}}(c)$.
\item \emph{Chiral quantum groups beyond the formal disk.} The
 infinitesimal elliptic $\mathfrak{sl}_2$ statement follows from the
 Felder $R$-matrix, KZB, and Fay trisecant identity. The
 finite-$\hbar$ obstruction is pentagon coherence. On
 $\mathbb P^1\times\mathbb P^1$, the carrier is the global
 factorization-algebra structure after passage to the pro-ambient
 class~M closure. At genus~$2$, the assertion of
 Conjecture~\ref{conj:g2-ddybe} is finite-$\hbar$ commutativity of
 the doubly-dynamical Casimirs; only the infinitesimal heat-equation
 symmetry is proved.
\item \emph{Non-formal $\mathrm{CY}_3$ chain model.} The Vol~III
 infinity-categorical construction is not a Vol~I proof input. The
 chain-level carrier is an
 $A_\infty$-compatible $S^3$-framing on $HC^-_3(C)$ for a non-formal
 Calabi--Yau threefold category~$C$.
\item \emph{Universal modular factorization envelope.} The envelope
 construction $L\mapsto U_X^{\mathrm{mod}}(L)$ is proved in
 Theorem~\ref{thm:platonic-adjunction}. The comparison boundary is the
 adjunction
 $U_X^{\mathrm{mod}}\dashv\operatorname{Prim}^{\mathrm{mod}}$
 of Conjecture~\ref{conj:universal-modular-factorization-envelope}
 and extension of the envelope--shadow functor beyond cyclically
 admissible Lie conformal inputs.
\end{enumerate}

\begin{conjecture}[Celestial quartic normalization]
\label{conj:celestial-cross-conjecture-vol1}
\ClaimStatusConjectured
\index{celestial OPE!cross-conjecture relation|textbf}
\index{quartic shadow!celestial cross-conjecture}
For quartic OPE data satisfying $\mathrm{SU}(2)$ covariance and HPL
antisymmetry, the ordered-to-symmetric averaging normalization is
conjecturally
\begin{equation}\label{eq:celestial-cross-conjecture}
Q^{\mathrm{sym}}_{110} - Q^{\mathrm{ord}}_{110}
\;=\;
-\,\frac{B_{\mathrm{mix}}}{10}
\;=\;
\frac{11}{90}
\end{equation}
after the Vol~II charged quartic jet conjecture and the Vol~II first
mixed bubble coefficient conjecture identify
$B_{\mathrm{mix}}=-11/9$. Vol~I does not assert a proof of the
normalization factor~$-1/10$.
\end{conjecture}

\begin{remark}[Normalization obligation]
The genus-$0$ quartic shadow
$R^{\mathrm{mod}}_{4,0,4}(\cA)$ admits a decomposition
into single-trace and multi-trace contributions
(Construction~\ref{constr:exchange-diagram-quartic}).
The symmetric jet $Q^{\mathrm{sym}}_{110}$ sums over all
$S_4$-orderings; the ordered jet $Q^{\mathrm{ord}}_{110}$
fixes one cyclic ordering. Their difference is a sum over
non-cyclic exchange diagrams with coefficients proportional to
$B_{\mathrm{mix}}$. The open mathematical condition is the normalization of this
exchange sum under the actual ordered-to-symmetric averaging map; a
bare count of $S_4/\mathbb Z_4$ cosets is not a proof of the
coefficient.
\end{remark}

\begin{conjecture}[Strict Koszul boundary]
\label{conj:koszul-swampland}
\ClaimStatusConjectured
\index{Koszul locus!strict boundary}
\index{Koszul conductor!strict boundary}
\index{bar-cobar inversion!strict boundary}
Let $\operatorname{Kosz}(X)$ be the strict locus on which the
bar-cobar counit
$\Omega\barB(\cA)\xrightarrow{\sim}\cA$ is a quasi-isomorphism in
the ordinary chain ambient. The complement of
$\operatorname{Kosz}(X)$ is conjecturally detected by persistent
off-diagonal classes in the bar-cobar spectral sequence. The scalar
function on a Koszul pair is
\[
K_\kappa(\cA,\cA^!) := \kappa(\cA) + \kappa(\cA^!).
\]
On the scalar Verdier surface where the Koszul partner and conductor
have been constructed, Proposition~\ref{prop:complementarity-landscape}
and Proposition~\ref{prop:bp-complementarity} give the values
$0$, $13$, $(H_N-1)K_N$ for principal $\mathcal W_N$, and $98/3$
for Bershadsky--Polyakov. Thus principal $\mathcal W_3$ gives
$250/3$, while principal $\mathcal W_4$ gives $533/2$ and already
lies outside the finite Theorem~C landmark buckets. The conjectural
assertion is that admissible affine quotients, minimal-model
class~M points, and any input whose bar-cobar spectral sequence has
persistent off-diagonal classes lie outside the strict locus. This
does not exclude completed, pro-object, or coderived reconstruction.
\end{conjecture}

\begin{remark}[Strict boundary evidence]
\label{rem:koszul-swampland-evidence}
\index{Koszul locus!strict boundary evidence}
Three local anchors constrain the strict boundary statement.

First, bar-cobar inversion is strict on the Koszul locus
and fails off it
(Theorem~\ref{thm:bar-cobar-inversion-qi}).
The failure mechanism is explicit: at an admissible level
$k = -2 + p/q$ for $\widehat{\mathfrak{sl}}_2$, the
vacuum Verma module acquires a singular vector at
conformal weight $(p-1)q$ in the bar-relevant range; passing
to the simple quotient $L_k(\mathfrak{sl}_2)$ kills this
vector, creating off-diagonal bar cohomology; the bar-cobar
spectral sequence fails to collapse, and the counit is not a
quasi-isomorphism
(Example~\ref{ex:admissible-sl2-failure}).
At the critical level $k = -h^\vee$, the Feigin--Frenkel
center produces infinitely many off-diagonal classes, and
inversion fails categorically.

Second, the scalar complementarity $\varkappa := \kappa + \kappa'$
(labelled $K_\kappa$ below; distinct from the central-charge
conductor $K^c := c+c^!$) is level-independent on the rows where the
Verdier partner and conductor have been verified
(Proposition~\ref{prop:complementarity-landscape},
Remark~\ref{rem:level-independence-landscape}).
It depends on the root datum or conformal-weight polynomial of the
Koszul pair, not on the particular level. The scalar values used
here are:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{@{}lll@{}}
Family & $K_\kappa = \kappa + \kappa'$ & Source \\
\midrule
Heisenberg, KM, free, lattice & $0$ &
 Prop.~\ref{prop:complementarity-landscape} \\
$\mathrm{Vir}_c$ & $13$ &
 Prop.~\ref{prop:complementarity-landscape} \\
$\cW_3$ & $250/3 \approx 83$ &
 Prop.~\ref{prop:complementarity-landscape}(iii) \\
$\cW_4$ & $533/2 = 266.5$ &
 Prop.~\ref{prop:complementarity-landscape}(iii) \\
Bershadsky--Polyakov ($\kappa$-sum) & $98/3 \approx 33$
 & Prop.~\ref{prop:bp-complementarity} \\
Bershadsky--Polyakov ($c$-sum) & $196$
 & Prop.~\ref{prop:bp-complementarity} \\
\end{tabular}
\end{center}
The monotone growth in $N$ for the $\cW_N$ series
($K_\kappa(\cW_N) = (H_N-1)K_N$ with
$K_N = 4N^3 - 2N - 2$, leading term $\sim 4N^3 \log N$)
records increasing scalar complementarity along the principal tower.

Third, the scalar equation $c_* = K_N/2$ is the unique point on the
principal line at which $\kappa(\cA) = \kappa(\cA^!)$
(Remark~\ref{rem:self-dual-complementarity}). When the Koszul
self-duality isomorphism $\cA\simeq\cA^!$ is available, the
complementarity decomposition has equal-dimensional halves and
Theorem~\ref{thm:self-dual-halving} gives the genus-$g$ splitting.
The Virasoro self-dual point $c = 13$ is the centre of
the interval $[0, 26]$; the critical dimension $c = 26$
is the boundary where $\kappa(\mathrm{Vir}_{26}^!) = 0$
and the dual curvature vanishes.
These are different phenomena: $c = 13$ is duality
equilibrium; $c = 26$ is dual uncurving.

The global detection statement is precisely the assertion that every
off-strict point is witnessed by an off-diagonal bar-cobar class.
The completed and coderived lanes are separate theorem
surfaces and are not negated by this conjecture.
\end{remark}

% ======================================================================

\section{Computational carriers}
\label{sec:frontier-research-notes}
\index{computational carriers|textbf}

The computations below are local carriers for the proved multi-weight
and CohFT statements. They are not additional theorem packages.

\subsection{The barbell graph and cross-channel arithmetic}
\label{subsec:barbell-research-notes}

The barbell graph (the 7th stable graph of
$\overline{\mathcal{M}}_{2,0}$: two genus-$0$ vertices with
self-loops connected by a bridge, $|\mathrm{Aut}| = 8$) has a
distinctive arithmetic property: its cross-channel contribution
$21/(4c)$ dominates at moderate central charge. At $c = 10$, the
barbell accounts for $39\%$ of the total cross-channel correction,
exceeding both the banana ($22\%$) and the theta ($34\%$). Only the
tadpole's $c$-independent $1/16$ eventually dominates, in the
semiclassical limit $c \to \infty$.

The $c$-independent tadpole piece arises from the cancellation
$C_{TWW} \cdot \eta^{TT} = c \cdot (2/c) = 2$: the OPE structure
constant and the propagator produce a pure number. This reflects the
conformal Ward identity constraining $C_{TWW}$ to be proportional to
the central charge. The topological residue $1/16$ is the product of
this Ward-identity cancellation with the genus-$1$ universal amplitude
$\kappa_T/24 = c/(2 \cdot 24)$ and the automorphism factor
$1/|\mathrm{Aut}|$.

\begin{question}\label{q:genus3-cross-channel}
Proposition~\ref{prop:w3-genus3-cross-channel} gives
\[
\delta F_3^{\mathrm{cross}}(\cW_3)
=
\frac{5c^3 + 3792c^2 + 1149120c + 217071360}{138240\,c^2}.
\]
Refine this closed form into a graph-by-graph stable-graph
decomposition over the $42$ genus-$3$ graphs of
$\overline{\mathcal M}_{3,0}$. Which graphs contribute nonzero
mixed-channel terms, and which contribution is forced by the
genus-$2$ barbell mechanism?
\end{question}

\begin{question}\label{q:propagator-ratio-invariant}
The propagator ratio $r_{ij} = \eta^{jj}/\eta^{ii}$ controls
cross-channel mixing: when $r_{ij} = 1$ for all pairs, the
multi-channel system is effectively single-channel and universality
holds. For $\cW_3$: $r_{TW} = 3/2$. Is there an algebraic
characterization of the locus $r_{ij} = 1$ in the space of
multi-weight chiral algebras? For $\cW_N$, is $r_{ij}$ determined
by the exponents of $\mathfrak{sl}_N$?
\end{question}

\subsection{Integrable hierarchies and the cross-channel gap}
\label{subsec:integrable-cross-channel-notes}

The integrable hierarchy (KdV for Virasoro, Boussinesq for $\cW_3$,
$N$-th Gelfand--Dickey for $\cW_N$) determines the per-channel genus
expansion $F_g^{\mathrm{diag}} = \kappa \cdot \lambda_g^{\mathrm{FP}}$
but \emph{not} the cross-channel correction. The cross-channel
correction arises from the multi-channel Feynman rules of the stable
graph sum, not from the spectral curve of the integrable hierarchy.
This separation (integrable on the diagonal, non-integrable
off-diagonal) instantiates the principle that the shadow obstruction
tower extends beyond the KdV hierarchy
(Remark~\ref{rem:shadow-multiplicative-deformation}).

\subsection{D-module purity: the BPZ Hitchin connection}
\label{subsec:bpz-hitchin-notes}

The D-module purity converse is proved for affine Kac--Moody algebras
via the Hitchin connection, which endows the KZ local system with a
variation of Hodge structure. For Virasoro and $\cW$-algebras, the
carrier is the BPZ system and the boundary is the first VHS axiom that
holds or fails.

\begin{question}\label{q:bpz-hitchin}
Does the BPZ system on
$\operatorname{Conf}_n(\mathbb{P}^1)$ underlie a variation of
Hodge structure? The KZ system has a natural VHS from the Hitchin
connection on the moduli of flat bundles (Axelrod--della
Pietra--Witten). Is there an analogous geometric structure for
conformal blocks of the Virasoro algebra? If not, identify the first
failed VHS axiom: regular singularity, quasi-unipotent monodromy,
polarization, or existence of a Hodge filtration preserved by the
connection.
\end{question}

\subsection{Shadow CohFT axiomatics}
\label{subsec:shadow-cohft-axiomatics-notes}

The shadow CohFT (Theorem~\ref{thm:shadow-cohft}) satisfies
equivariance and splitting unconditionally, but the flat identity
(string equation) requires the vacuum to lie in the generating
space~$V$. The rank-$1$ string equation is proved unconditionally via
the DR hierarchy (Buryak's forgetful property of DR cycles,
Section~\ref{subsec:dr-hierarchy-string}).

\begin{question}\label{q:modified-cohft}
What is the correct axiom system for a CohFT without flat unit?
The modified string equation with $\psi$-class corrections from the
$R$-matrix provides a replacement. Is there a ``non-unital CohFT''
framework analogous to non-unital $A_\infty$ algebras, where the
unit axiom is replaced by a homotopy-unit structure?
\end{question}

% ======================================================================

\section{Cross-volume comparison maps}
\label{sec:cross-volume-bridges}
\index{cross-volume comparison maps|textbf}

The Vol~I theorems are statements about chiral algebras on curves,
their bar coalgebras, Verdier-side Koszul duals, modular MC classes,
and chiral Hochschild derived centres. Vol~II supplies
holomorphic-topological and PVA compatibility data. Vol~III supplies
Calabi--Yau sources for families of $E_1$-chiral shadows. Neither
volume is a proof input for a Vol~I theorem unless the statement is
explicitly cited as an external hypothesis.

The Vol~III specialization has a strict boundary condition. A
Calabi--Yau category first maps to a holomorphic factorization algebra;
after integration over a cycle $\Sigma_{d-1}$ and restriction to a
reference curve~$C$, it gives an $E_1$-chiral shadow on~$C$. Theorem~A
applies to that shadow on~$C$, not to the original Calabi--Yau category
before specialization.

The cross-volume boundary consists of typed comparison maps:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Vol~II: the class-$\mathsf M$ comparison
 $\chi_{\mathrm{cel}}^{\mathsf M}$ from the completed/coderived
 universal celestial object to the gravitational branch. Its
 obstruction is descent to the bounded direct-sum chain ambient.
\item Vol~II: the super-complementarity pairing
 $\Pi_{\mathrm{Ber}}$ between super-trace and Berezinian
 normalizations on the sub-Sugawara super-Yangian line.
\item Vol~II: the zero-twisted-evolution correction tensor $T_{ijk}$,
 together with the chain homotopy carrying its propagation law.
\item Vol~III: the comparison carrier
 $\mathsf{HD}_{K3}^{\mathrm{orth}}$ is the non-abelian K3 chiral
 Hall--Drinfeld double attached to the orthogonal Mukai target. Its
 construction obligation is separation of the ADE/Kummer Yangian slices
 $Y_{\hbar}(\mathfrak{so}(4,20))$ from the conditional non-Kac
 Hodge-parity refinement $Y_{\hbar}(\mathfrak{so}(4|20))$.
\item Vol~III: the chain map $\mu_{\mathrm{Muk}}$ transporting the
 Mukai pairing from the Kummer step-$5$c residue to the signature
 $(4,20)$ form.
\end{enumerate}

% ======================================================================
% Cross-reference labels.
% ======================================================================
\label{sec:concordance-non-principal-w}
\label{sec:concordance-e1-modular-theory}
\label{sec:concordance-structural-upgrades}
\label{sec:concordance-analytic-sewing}
\label{subsec:concordance-koszulness-meta-theorem}
\label{subsec:concordance-shadow-depth-classes}
\label{subsec:concordance-further-characterizations}
\label{subsec:concordance-bifunctor-obstruction}
\label{subsec:concordance-koszulness-xref}
\label{subsec:concordance-computational-diagnostics}
\label{subsec:coderived-ran}
\label{subsec:completion-kinematics-theory}
\label{subsec:analytic-completion-theory}
\label{sec:concordance-arithmetic-sewing}

% ======================================================================
% Additional cross-reference labels.
% ======================================================================
\label{sec:principal-contributions}
\label{rem:four-levels}
\label{subsec:anomaly-koszul}
\label{subsec:vassiliev}
\label{rem:en-scope}
\label{rem:proof-obstructions}
\label{rem:structural-gaps}
\label{rem:cat-o-generation-obstruction}

% Concordance theorem and conjecture labels.
\phantomsection\label{thm:family-index}
\phantomsection\label{thm:universal-MC}
\phantomsection\label{thm:volume-one-concrete-modular-datum}
\phantomsection\label{thm:master-theta}
\phantomsection\label{thm:master-pbw}
\phantomsection\label{thm:discriminant-spectral}
\phantomsection\label{thm:lagrangian-complementarity}
\phantomsection\label{thm:anomaly-koszul}
\phantomsection\label{conj:derived-drinfeld-kohno-outlook}
\phantomsection\label{conj:categorical-modular-kd-outlook}
\phantomsection\label{conj:cumulant-recognition-outlook}
\phantomsection\label{conj:ads-cft-bar-outlook}
\phantomsection\label{conj:master-dk-kl-outlook}
\phantomsection\label{conj:v1-master-infinite-generator-outlook}
\phantomsection\label{conj:v1-master-bv-brst-outlook}
\phantomsection\label{conj:anomaly-physical-outlook}
\phantomsection\label{conj:v1-vassiliev-bar-outlook}
\phantomsection\label{conj:jet-principle-outlook}
\phantomsection\label{conj:standard-tower-mc5-reduction-outlook}
\phantomsection\label{prop:vassiliev-genus0}
\phantomsection\label{cor:standard-tower-mc5-closure-outlook}
\phantomsection\label{def:cumulant-coalgebra-outlook}
\phantomsection\label{def:spectral-branch-object-outlook}
\phantomsection\label{comp:spectral-discriminants-standard-outlook}
\phantomsection\label{eq:modular-cumulant-transform}
