% Introduction supplement: Twisted Holography and Quantum Gravity.
% Develops the holographic modular Koszul datum from foundations.
% Builds the bulk-boundary-line triangle, collision filtration, shadow
% connection, Yangian extraction, and Arnold-to-YBE proof as
% self-contained mathematical constructions.

% ======================================================================
% SECTION 1: THE HOLOGRAPHIC TRIANGLE
% ======================================================================

\section{The holographic triangle}
\label{sec:holographic-triangle}
\index{holographic triangle|textbf}
\index{bulk-boundary-line triangle|textbf}

Three algebraic objects attach to a chiral algebra~$\cA$ on a smooth
projective curve~$X$. They form a triangle whose vertices are the
boundary algebra, the cochain-level closed-sector slot, and the
line-operator category. In this section the word \emph{bulk} names the
chiral Hochschild derived-centre slot. A physical three-dimensional
holomorphic-topological bulk is a separate factorization algebra
equipped with a closed-open comparison map into that slot.

\begin{definition}[Supplement algebraic-sector register;
\ClaimStatusDefinitional]
\label{def:supp-algebraic-sector-register}
\textit{Type signature.}
Quadrant: Open. Presentation: chain-level + $(\infty,1)$.
Level: $1 \to 3$ (chart $\to$ chiral derived-centre slot).
Hypothesis package: augmented chiral algebra $\cA$ on a smooth
projective curve~$X$.
\medskip

The holographic register inscribed here is the \emph{algebraic
sector}. Boundary, closed-sector, and interaction are functorial
constructions attached to~$\cA$:
\begin{equation}\label{eq:supp-algebraic-sector}
\partial \;=\; \cA, \qquad
\mathrm{closed} \;=\; Z^{\mathrm{der}}_{\mathrm{ch}}(\cA), \qquad
\mathrm{interaction} \;=\; \mathsf{SC}^{\mathrm{ch,top}}\text{-brace}.
\end{equation}
The closed-sector slot $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)
= R\mathcal{H}om_{\cA\text{-bimod}}(\cA, \cA)$ is the chiral Hochschild
endomorphism algebra; the brace structure is the
$\mathsf{SC}^{\mathrm{ch,top}}$ two-colour action on the derived-centre
pair $(Z^{\mathrm{der}}_{\mathrm{ch}}(\cA), \cA)$ inscribed in
Volume~II. The triangle does not construct a compact dynamical-metric
path integral. The level-5 modular-shadow scalars
(modular form, $\kappa$-tuple, partition function) are obtained from
the level-4 brane/operator algebra by modular trace and clutching;
the reverse direction is the operator-level Pfaffian /
square-root reconstruction problem and remains open. A gravity-line
completion to a compact dynamical-metric path integral requires
the BTZ / Cardy / Maloney--Witten / Manschot--Moore Farey-tail
hypothesis package: modular invariance of the boundary partition
function, vacuum (identity-block) dominance in the high-temperature
channel, saddle stability of the gravitational instanton, and the
Maloney--Witten Farey-tail completion of the $\mathrm{SL}(2,
\mathbb{Z})$-orbit sum.
\end{definition}

Throughout this section $\cA$ is augmented, and it is modular Koszul
whenever the genus-completed Maurer--Cartan element is invoked. The
strict symbols $\cA^!$ and $\mathsf{Line}(\cA)$ are used only on the
finite-type Verdier/Koszul comparison locus, or after passage to a
completed continuous dual satisfying the Mittag--Leffler and
separatedness hypotheses. Shifted-symplectic and Lagrangian statements
also require the perfectness and non-degenerate Verdier-pairing
hypotheses stated in Theorem~\ref{thm:quantum-complementarity-main}
and Proposition~\ref{prop:ptvv-lagrangian}.

\subsection{Boundary algebra}
\label{subsec:vertex-boundary}
\index{boundary algebra|textbf}

Let $(\cA, \varepsilon \colon \cA \to \omega_X)$ be an augmented
chiral algebra on~$X$. The \emph{boundary algebra} is $\cA$ itself:
an augmented $\mathcal{D}_X$-module equipped with a chiral bracket
\begin{equation}\label{eq:supp-boundary-chiral-bracket}
\mu^{\mathrm{ch}} \colon j_* j^*(\cA \boxtimes \cA)
\longrightarrow \Delta_!(\cA),
\end{equation}
where $j \colon X^2 \setminus \Delta \hookrightarrow X^2$ is the
complement of the diagonal. The boundary algebra carries the full
OPE data: for sections $a, b \in \cA$ and local coordinates $z, w$,
\[
a(z)\, b(w) \;\sim\;
\sum_{n \geq 0} \frac{(a_{(n)} b)(w)}{(z - w)^{n+1}}.
\]
The maximal pole order $N(a,b) = \max\{n : a_{(n)}b \neq 0\}$ and
the conformal grading $\Delta \colon \cA \to \cA$ (eigenvalue
decomposition of $L_0$) are part of the input data.
The boundary algebra is the starting point; the other two vertices are
constructed from it.

\subsection{Closed-sector algebra: chiral derived centre}
\label{subsec:vertex-bulk}
\index{closed-sector algebra|textbf}
\index{derived centre|textbf}

The algebraic \emph{closed-sector slot} is the chiral derived centre of~$\cA$:
\begin{equation}\label{eq:supp-chiral-derived-centre-def}
\mathbf{C}_{\mathrm{ch}}(\cA)
\;:=\;
Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)
\;=\;
R\mathcal{H}om_{\cA\text{-bimod}}(\cA,\, \cA).
\end{equation}
Define the centre local system on the universal curve
$\pi \colon \mathcal{C}_g \to \overline{\mathcal{M}}_g$ by
\begin{equation}\label{eq:supp-center-local-system-def}
\mathcal{Z}(\cA) \;:=\;
R\mathcal{H}om_{\cA\text{-bimod}}(\cA,\, \cA),
\end{equation}
where the bimodule structure uses left and right chiral actions.
On a fixed smooth curve~$\Sigma_g$ of genus~$g$, the fiber of the
centre local system is
\[
Z(\cA|_{\Sigma_g}) \;=\;
\operatorname{End}_{\cA\text{-bimod}}(\cA|_{\Sigma_g})
\;\cong\;
H^0(\Sigma_g,\, Z_{\mathrm{ch}}(\cA)),
\]
the space of chiral-central sections: those $\phi \in \cA$ satisfying
$\phi_{(n)} a = 0$ for all $a \in \cA$ and all $n \geq 0$. This is
Hochschild cohomological centre data, not the zeroth Zhu algebra and
not the chiral abelianization $\cA/[\cA,\cA]_{\mathrm{ch}}$. The
Virasoro vector belongs to the boundary OPE data; it is central only
when its non-negative modes vanish on~$\cA$.

The \emph{ambient complex} at genus~$g$ is the derived global sections
of the centre local system:
\begin{equation}\label{eq:supp-ambient-complex-def}
\mathbf{C}_g(\cA) \;:=\;
R\Gamma(\overline{\mathcal{M}}_g,\, \mathcal{Z}(\cA)).
\end{equation}
On the perfect Verdier comparison locus this complex carries the
shifted-symplectic structure supplied by Verdier duality on the centre
\textup{(}Proposition~\ref{prop:ptvv-lagrangian}\textup{)}. If the
Verdier--Koszul involution is represented by a cochain involution
$\sigma$ on $\mathbf{C}_g(\cA)$, Theorem~\ref{thm:quantum-complementarity-main}
gives the homotopy eigenspace decomposition
\begin{equation}\label{eq:supp-complementarity-eigenspaces}
\mathbf{C}_g(\cA)
\;\simeq\;
\mathbf{Q}_g(\cA) \oplus \mathbf{Q}_g(\cA^!),
\end{equation}
where $\mathbf{Q}_g(\cA) = \operatorname{fib}(\sigma - \mathrm{id})$
and $\mathbf{Q}_g(\cA^!) = \operatorname{fib}(\sigma + \mathrm{id})$
are the $+1$ and $-1$ homotopy eigenspaces. Under the additional
non-degenerate anti-invariant Verdier pairing hypothesis, each
eigenspace is Lagrangian for the shifted-symplectic pairing. The
decomposition~\eqref{eq:supp-complementarity-eigenspaces} is the
Theorem~C surface used here; its Lagrangian upgrade is conditional on
the stated pairing hypotheses.

The genus-$g$ ambient complex extracted from the chiral derived centre
is $\mathbf{C}_g(\cA)$. The protected holographic transform
$\mathbb{H}_X(\cA) = \mathbb{D}_{\operatorname{Ran}}
\circ \barB_X(\cA)$
(Definition~\ref{def:frontier-protected-holographic-transform})
lands, on the strict finite-type or completed Koszul locus, in the
Verdier/Koszul dual branch $\cA^!$
(Theorem~\ref{thm:frontier-protected-bulk-antiinvolution}). This
does not identify the centre $\mathbf{C}_{\mathrm{ch}}(\cA)$ with
$\cA^!$, and it does not construct a physical holomorphic-topological
bulk.

\subsection{Line-operator category}
\label{subsec:vertex-lines}
\index{line-operator category|textbf}
\index{Koszul dual!module category}

On the strict Verdier/Koszul line locus, the \emph{line-operator
category} is the derived module category of the Koszul dual algebra:
\begin{equation}\label{eq:supp-line-category-def}
\mathsf{Line}(\cA) \;:=\; \cA^!\text{-}\mathsf{mod}.
\end{equation}
Here $\cA^i=H^*(\barB_X(\cA))$ is the cohomological
Koszul-dual coalgebra, and
$\cA^! = (\cA^i)^\vee$ is the strict Koszul dual chiral algebra
under the stated finite-type or completed continuous duality
convention. The bar--cobar map
$\Omega_X\barB_X(\cA)\to\cA$ is inversion, not Koszul duality.
Separately,
$\mathbb{D}_{\operatorname{Ran}}\barB_X(\cA)$ is the homotopy
Koszul-dual factorization algebra. The module category
$\cA^!\text{-}\mathsf{mod}$ is a
$\mathbb{C}$-linear dg category whose objects are $\cA^!$-modules
(factorization modules on $\operatorname{Ran}(X)$) and whose morphisms
are chain maps.

After the line-kernel comparison, the category $\mathsf{Line}(\cA)$
carries a meromorphic tensor structure: for
$M, N \in \cA^!\text{-}\mathsf{mod}$, the tensor product
$M \otimes_{r(z)} N$ is defined by the fusion product along the
spectral parameter~$z$. Before this comparison the binary collision
residue is a kernel in $\mathrm{End}_{\cA}(2)[\![z^{-1}]\!]$; on the
line side it is written as an $r$-matrix
$r(z) \in \cA^! \,\widehat{\otimes}\, \cA^![\![z^{-1}, z]\!]$.
The tensor structure is \emph{meromorphic}: the poles of $r(z)$ in
the spectral parameter produce non-trivial monodromy, and the
category is not genuinely braided but carries an $\Eone$-monoidal
structure (ordered configurations on $\mathbb{R} \subset \mathbb{C}$).

For affine Kac--Moody $\cA = \widehat{\fg}_k$ at non-critical level
$k \neq -h^\vee$, on the Kazhdan--Lusztig comparison surface the
Koszul dual is
$\cA^! \simeq \mathrm{CE}^{\mathrm{ch}}(\widehat{\fg}_{k'})$ with
$k' = -k - 2h^\vee$. The identification of the corresponding
line-operator category with the Kazhdan--Lusztig category is a separate
comparison theorem on this surface:
\begin{equation}\label{eq:supp-line-kl-identification}
\mathsf{Line}(\widehat{\fg}_k)
\;\simeq\;
\mathcal{O}_{k'}(\widehat{\fg})
\;\simeq\;
\mathcal{C}(U_q(\fg)),
\end{equation}
where $q = e^{\pi i/(k + h^\vee)}$ and the last equivalence is the
Kazhdan--Lusztig theorem
(Theorem~\ref{thm:kazhdan-lusztig-equivalence}).

\subsection{The triangle diagram}
\label{subsec:triangle-diagram}

The three vertices assemble into a typed diagram of algebraic outputs
and comparison maps:
\begin{equation}\label{eq:supp-holographic-triangle-diagram}
\begin{tikzcd}[row sep=huge, column sep=huge]
& \text{Bulk: } \mathbf{C}_g(\cA)
 \arrow[dl, "\text{closed action}"']
 \arrow[dr, "\text{dual shadow}"]
& \\
\text{Boundary: } \cA
 \arrow[rr, "\text{bar cohomology + Verdier}"']
 \arrow[ur, "\text{bar trace}"]
& & \text{Lines: } \mathsf{Line}(\cA)
\end{tikzcd}
\end{equation}
The upward edge is the bar construction followed by the trace into the
centre local system: $\barB_X(\cA)$ supplies the bar coalgebra, and
its cohomology is $\cA^i$ before Verdier dualization. The downward
edge is the closed action of the chiral Hochschild endomorphism algebra
on its boundary object~$\cA$; it is algebraic closed-sector action,
not a physical closed-open map from a quantum field theory. The right
edge is the holographic cofiber:
$\mathbf{H}_g^{\mathrm{hol}}(\cA) =
\operatorname{cofib}(\mathbf{Q}_g(\cA) \to \mathbf{C}_g(\cA))
\simeq \mathbf{Q}_g(\cA^!)$
(Theorem~\ref{thm:frontier-protected-bulk-antiinvolution}(iii)).
The bottom edge is Koszul duality: $\cA \mapsto \cA^i \mapsto \cA^!$
by bar cohomology followed by finite-type or completed duality, with
the module category
$\cA^!\text{-}\mathsf{mod}$ as the categorical output.

The algebraic datum below records these distinct outputs together with
the single Maurer--Cartan element~$\Theta_\cA$ that controls their
modular collision structure.

\subsection{Holographic datum: the seven-entry package}
\label{subsec:holographic-datum-seven-entry}
\label{subsec:holographic-datum-sixfold}
\index{holographic modular Koszul datum|textbf}

The separation of the boundary algebra, the bar-cohomology coalgebra,
the strict Verdier/Koszul dual, and the chiral derived centre is
encoded by the \emph{holographic modular Koszul datum}:
\begin{equation}\label{eq:supp-holographic-datum-intro}
\mathcal{H}(\cA)
\;=\;
\bigl(\cA,\;\cA^i,\;\cA^!,\;\mathbf{C}_{\mathrm{ch}}(\cA),\;
r(z),\;\Theta_\cA,\;\nabla^{\mathrm{hol}}\bigr).
\end{equation}
The seven entries are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The boundary algebra $\cA$: augmented chiral algebra on~$X$.
\item The bar-cohomology coalgebra
 $\cA^i=H^*(\barB_X(\cA))$: the Koszul-dual coalgebra.
\item The strict line algebra $\cA^!=(\cA^i)^\vee$: strict
 finite-type or completed Verdier/Koszul-dual algebra of~$\cA$ under
 the stated hypotheses.
\item The bulk algebra
 $\mathbf{C}_{\mathrm{ch}}(\cA)=Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$:
 chiral derived centre of~$\cA$.
\item The spectral $r$-matrix $r(z)$: binary genus-zero collision
 residue of~$\Theta_\cA$ (extracted in \S\ref{subsec:collision-filtration-recovery}).
\item The modular MC element
 $\Theta_\cA \in \MC(\gAmod)$: bar-intrinsic positive-genus
 Maurer--Cartan element
 (Theorem~\ref{thm:mc2-bar-intrinsic}).
\item The modular shadow connection
 $\nabla^{\mathrm{hol}}_{g,n} = d - \operatorname{Sh}_{g,n}(\Theta_\cA)$:
 flat connection on the derived coinvariant / protected-state package
 when the shadow projection is defined and compatible with the MC
 bracket; it specializes to the corresponding derived conformal-block
 package on benchmark comparison surfaces
 (constructed in \S\ref{subsec:thqg-intro-shadow-connection-construction}).
\end{enumerate}
The line category $\mathsf{Line}(\cA)=\cA^!\text{-}\mathsf{mod}$ is
the module category attached to the third entry; it is not the fourth
entry. The bar, Verdier, and Hochschild entries are typed functorial
constructions from~$\cA$; they are not projections of
$\Theta_\cA$. The MC-dependent entries are constrained by the equation
\begin{equation}\label{eq:supp-mc-equation-holographic-intro}
D_\cA\,\Theta_\cA + \tfrac{1}{2}[\Theta_\cA, \Theta_\cA] \;=\; 0
\end{equation}
in the modular convolution dg~Lie algebra~$\gAmod$, and the single
identity $D_\cA^2 = 0$
(Theorem~\ref{thm:convolution-d-squared-zero}).

\begin{proposition}[Algebraic datum versus physical bulk;
\ClaimStatusProvedHere]
\label{prop:supp-algebraic-physical-bulk-separation}
\textit{Type signature.}
Quadrant: Open. Presentation: chain-level + $(\infty,1)$.
Level: $1 \leftrightarrow 2 \leftrightarrow 3$ (boundary chart, bar
twisting coalgebra, derived chiral centre).
Hypothesis package: augmented $\cA$ on a smooth projective curve;
finite-type or completed continuous duality conventions for
$\cA^!$; the closed-open comparison map
$\mathrm{CO}_\cA$ is additional data not included in
$\mathcal{H}(\cA)$.
\medskip

The datum $\mathcal{H}(\cA)$ determines the algebraic triangle
\[
\Omega_X\barB_X(\cA)\to\cA,\qquad
\mathbb{D}_{\operatorname{Ran}}\barB_X(\cA)\simeq\cA^!_\infty,\qquad
\mathbf{C}_{\mathrm{ch}}(\cA)=
R\mathcal{H}om_{\cA\text{-bimod}}(\cA,\cA),
\]
together with the line category on the strict comparison locus. It
does not determine a physical holomorphic-topological bulk
$\mathcal{O}^{\mathrm{HT}}_{\mathrm{bulk}}$ unless the extra
closed-open comparison datum
\[
\mathrm{CO}_\cA\colon
\mathcal{O}^{\mathrm{HT}}_{\mathrm{bulk}}\big|_X
\longrightarrow
\mathbf{C}_{\mathrm{ch}}(\cA)
\]
is included and required to be an equivalence in the chosen analytic or
coderived completion.
\end{proposition}

\begin{proof}
The bar-cobar counit has target~$\cA$, the Verdier dual of the bar
coalgebra has target the homotopy Koszul-dual factorization algebra,
and the chiral derived centre is the Hochschild endomorphism algebra of
$\cA$ as a bimodule over itself. These constructions have different
source and target categories. A physical bulk is additional closed
factorization data. If $\mathcal{B}$ is a non-acyclic closed
factorization algebra with zero boundary action, then adjoining
$\mathcal{B}$ as a decoupled closed summand changes
$\mathcal{O}^{\mathrm{HT}}_{\mathrm{bulk}}$ but leaves the boundary
algebra, the bar complex, $\cA^i$, $\cA^!$,
$\mathbf{C}_{\mathrm{ch}}(\cA)$, $r(z)$, $\Theta_\cA$, and the shadow
connection attached to~$\cA$ unchanged. The algebraic datum therefore
cannot distinguish the two physical closed sectors. The ambiguity is
removed only after the closed-open map is part of the data and is an
equivalence in the stated completion.
\end{proof}

\input{chapters/connections/thqg_introduction_supplement_body}
