% Concordance supplement: sixteen gravitational results (G1)--(G16).
% Pure data table.  No prose.

¥section{Twisted holography and quantum gravity programme}
¥label{sec:concordance-thqg}
¥index{concordance!twisted holography programme}

¥begin{center}
¥renewcommand{¥arraystretch}{1.35}
¥small
¥begin{tabular}{clp{5cm}lp{3.8cm}l}
& ¥textbf{Result} & ¥textbf{Statement} & ¥textbf{Status} & ¥textbf{Dependencies} & ¥textbf{File} ¥¥
¥hline
¥textbf{G1}
  & Finiteness
  & Genus-$g$ amplitudes finite at every arity; no UV renormalization
  & ¥ClaimStatusProvedHere
  & Thm A, ¥ref{thm:general-hs-sewing}, ¥ref{lem:arity-cutoff}, ¥ref{thm:recursive-existence}
  & ¥texttt{thqg¥_pert.} ¥¥
¥textbf{G2}
  & Complexity
  & $r_{¥max}(¥cA)$ controls bulk $L_¥infty$ complexity; G/L/C/M
  & ¥ClaimStatusProvedHere
  & ¥ref{def:shadow-depth-classification}, ¥ref{prop:shadow-formality-low-arity}
  & ¥texttt{thqg¥_grav¥_c.} ¥¥
¥textbf{G3}
  & Polarization
  & $¥mathbf{C}_g ¥simeq ¥mathbf{Q}_g(¥cA) ¥oplus ¥mathbf{Q}_g(¥cA^!)$, Lagrangian
  & ¥ClaimStatusProvedHere
  & Thm C, ¥ref{prop:ptvv-lagrangian}, ¥ref{thm:ambient-complementarity-fmp}
  & ¥texttt{thqg¥_symp.} ¥¥
¥textbf{G4}
  & $S$-duality
  & $¥cA ¥leftrightarrow ¥cA^!$ exchanges strong/weak coupling
  & ¥ClaimStatusProvedHere
  & G3, Thm D
  & ¥texttt{thqg¥_grav¥_s.} ¥¥
¥textbf{G5}
  & Yangian
  & $r(z)$ satisfies CYBE; $¥cA^!¥text{-}¥mathsf{mod}$ gives lines, with the dg-shifted-Yangian lane affine / evaluation-core
  & ¥ClaimStatusProvedHere
  & Thm A, MC3 (evaluation core)
  & ¥texttt{thqg¥_grav¥_y.} ¥¥
¥textbf{G6}
  & Soft graviton
  & Shadow connection Ward $¥to$ BMS soft theorems at arity $2$
  & ¥ClaimStatusProvedHere
  & G2, G3
  & ¥texttt{thqg¥_soft.} ¥¥
¥textbf{G7}
  & Bootstrap
  & Genus spectral seq.¥ gives inductive constraints on $Z_g$
  & ¥ClaimStatusProvedHere
  & G1, G6, MC5
  & ¥texttt{thqg¥_mod.} ¥¥
¥textbf{G8}
  & Reconstruction
  & $¥mathcal{H}(¥cA)$ reconstructed from boundary OPE
  & ¥ClaimStatusProvedHere
  & G1--G7
  & ¥texttt{thqg¥_holo.} ¥¥
¥textbf{G9}
  & Critical string
  & $c = 26$: NAP datum $¥mathrm{Vir}_{26}^! = ¥mathrm{Vir}_0$, resonance saturation (self-dual at $c = 13$)
  & ¥ClaimStatusProvedHere
  & G2, G4
  & ¥texttt{thqg¥_crit.} ¥¥
¥textbf{G10}
  & Fredholm
  & $Z_g(¥cA) = ¥det(1 - K_g)$; HS for standard landscape
  & ¥ClaimStatusProvedHere
  & G1, G7, ¥ref{thm:heisenberg-sewing}
  & ¥texttt{thqg¥_fred.} ¥¥
¥hline
¥textbf{G10+}
  & Grav.¥ comp.
  & $F_g^{¥mathrm{sc}}(c) + F_g^{¥mathrm{sc}}(26{-}c) = 13¥lambda_g^{¥mathrm{FP}}$;
    $¥hat{A}$-genus gf; Borel radius $2¥pi/¥rho(c)$; self-dual at $c{=}13$
  & ¥ClaimStatusProvedHere
  & G10, Thm C, Thm D, ¥ref{thm:shadow-radius}
  & ¥texttt{thqg¥_fred.} ¥¥
¥hline
¥multicolumn{6}{l}{¥textit{Entanglement programme (G11--G16)}} ¥¥
¥hline
¥textbf{G11}
  & Ent.¥ entropy
  & $S_{¥mathrm{EE}}^{(g)}(¥cA)$ from $¥Theta_¥cA^{¥leq r}$;
    scalar $S_{¥mathrm{EE}}^{¥mathrm{sc}} = (c/3)¥log(L/¥varepsilon)$
  & ¥ClaimStatusHeuristic
  & Thm D, G2, G10
  & ¥texttt{thqg¥_ent.} ¥¥
¥textbf{G12$'$}
  & Quant.¥ ext.¥ surf.
  & Shadow extremality: $¥partial_A S_{¥mathrm{bulk}} + ¥partial_A S_{¥mathrm{EE}}^{¥mathrm{sc}} = 0$
    as shadow connection Ward identity
  & ¥ClaimStatusConjectured
  & G3, G6, G11
  & ¥texttt{thqg¥_ent.} ¥¥
¥textbf{G13}
  & Modular flow
  & $¥nabla^{¥mathrm{sh}}$-parallel transport $=$ modular flow;
    Verdier structural properties proved, identification with $J$ heuristic; full flow conjectural
  & ¥ClaimStatusConjectured
  & G4, G6
  & ¥texttt{thqg¥_ent.} ¥¥
¥textbf{G14}
  & Error correction
  & Bar-cobar code: entanglement wedge from open/closed pair
    $¥mathcal{U}(¥cA)$
  & ¥ClaimStatusProvedHere
  & Thm B, G3, G8
  & ¥texttt{thqg¥_ent.} ¥¥
¥textbf{G15}
  & Page constraint
  & $C_g(¥cA) + C_g(¥cA^!) = ¥dim¥cH_g(¥cA)$
    (Lagrangian capacity) from complementarity (Thm‾C)
  & ¥ClaimStatusProvedHere
  & Thm C, Thm D, G3
  & ¥texttt{thqg¥_ent.} ¥¥
¥textbf{G16}
  & Replica
  & $Z_n(¥cA) = ¥operatorname{tr}(¥rho_¥cA^n)$ via $n$-fold
    shadow sewing; analytic continuation heuristic
  & ¥ClaimStatusHeuristic
  & G10, G11, MC5
  & ¥texttt{thqg¥_ent.}
¥end{tabular}
¥end{center}

¥medskip

¥noindent¥textbf{Cross-reference matrix}: inputs from the proved core.

¥begin{center}
¥renewcommand{¥arraystretch}{1.3}
¥small
¥begin{tabular}{c|ccccc|ccccc|c}
& ¥textbf{A} & ¥textbf{B} & ¥textbf{C} & ¥textbf{D} & ¥textbf{H}
& ¥textbf{MC1} & ¥textbf{MC2} & ¥textbf{MC3} & ¥textbf{MC4} & ¥textbf{MC5}
& $¥Theta_¥cA$ ¥¥
¥hline
G1  & $¥bullet$ & & & & & & $¥bullet$ & & & $¥bullet$ & $¥bullet$ ¥¥
G2  & & & & & & $¥bullet$ & $¥bullet$ & & & & $¥bullet$ ¥¥
G3  & & & $¥bullet$ & & & & & & & & $¥bullet$ ¥¥
G4  & & & $¥bullet$ & $¥bullet$ & & & & & & & $¥bullet$ ¥¥
G5  & $¥bullet$ & & & & & & $¥bullet$ & $¥bullet$ & & & $¥bullet$ ¥¥
G6  & & & & & & & $¥bullet$ & & & & $¥bullet$ ¥¥
G7  & & & & & & & $¥bullet$ & & & $¥bullet$ & $¥bullet$ ¥¥
G8  & $¥bullet$ & $¥bullet$ & $¥bullet$ & $¥bullet$ & $¥bullet$
    & $¥bullet$ & $¥bullet$ & $¥bullet$ & $¥bullet$ & $¥bullet$
    & $¥bullet$ ¥¥
G9  & & & & $¥bullet$ & & & $¥bullet$ & & $¥bullet$ & & $¥bullet$ ¥¥
G10 & $¥bullet$ & & & & & & $¥bullet$ & & & $¥bullet$ & $¥bullet$ ¥¥
¥hline
G11 & & & & $¥bullet$ & & & $¥bullet$ & & & $¥bullet$ & $¥bullet$ ¥¥
G12$'$ & & & $¥bullet$ & & & & $¥bullet$ & & & & $¥bullet$ ¥¥
G13 & & & & $¥bullet$ & & & $¥bullet$ & & & & $¥bullet$ ¥¥
G14 & & $¥bullet$ & $¥bullet$ & & & & & & & & $¥bullet$ ¥¥
G15 & & & $¥bullet$ & $¥bullet$ & & & & & & & $¥bullet$ ¥¥
G16 & $¥bullet$ & & & & & & $¥bullet$ & & & $¥bullet$ & $¥bullet$
¥end{tabular}
¥end{center}
