% Status and semantic-level disputes are settled by Chapter 34 (concordance.tex).
\chapter{Bar and cobar constructions}
\label{chap:bar-cobar}


% [Governing question and H/M/S route remarks removed — content subsumed by introduction.]
\index{bar construction!as integral transform|textbf}
\index{non-abelian Fourier transform|textbf}

In conformal field theory, the operator product expansion encodes how local operators fuse when brought together on a Riemann surface.  The bar complex geometrizes this fusion: it replaces the algebraic OPE data with an integral transform over Fulton--MacPherson compactifications of configuration spaces, whose kernel is the logarithmic 1-form $\eta_{ij} = d\log(z_i - z_j)$ of \S\ref{sec:the-seed}.  The output is a factorization coalgebra $\barB(\cA)$ on $\operatorname{Ran}(X)$ with nilpotent differential ($d^2 = 0$) at genus~$0$: the additive shadow of the multiplicative OPE.  Verdier duality inverts the transform: $\Omega \circ \barB \xrightarrow{\sim} \mathrm{id}$ on the Koszul locus (Theorem~\ref{thm:bar-cobar-inversion-qi}), recovering the algebra from its nilpotent image---the categorical logarithm--exponential correspondence of Remark~\ref{rem:nilpotence-periodicity}.

The three-step bar differential
$d = d_{\mathrm{internal}} + d_{\mathrm{residue}}
+ d_{\mathrm{de\,Rham}}$ that we built by hand for the Heisenberg
algebra in Chapter~\ref{ch:heisenberg-frame} now receives its general
formulation.  The key structural insight is that the three components
correspond to three types of geometry on the compactified
configuration space $\overline{C}_n(X)$:
\begin{center}
\small
\begin{tabular}{lll}
\textbf{Component} & \textbf{Geometric origin} & \textbf{Extracts} \\
\hline
$d_{\mathrm{internal}}$ & Internal differential of $\cA$ & Algebraic structure \\
$d_{\mathrm{residue}}$ & Residues along collision divisors $D_{ij}$ & OPE coefficients \\
$d_{\mathrm{de\,Rham}}$ & de~Rham differential on $\overline{C}_n(X)$ & Configuration geometry
\end{tabular}
\end{center}

\noindent
The Arnold relation
(Theorem~\ref{thm:arnold-three}) ensures $d^2 = 0$: it is the
coherence condition that the geometry of collisions is consistent.
The genus-$0$ bar differential $\dzero$ satisfies $\dzero^2 = 0$
(Theorem~\ref{thm:bar-nilpotency-complete}), and Verdier duality
establishes $\mathbb{D}_{\operatorname{Ran}} \barB_X(\cA) \simeq
\barB_X(\cA^!)$.  The curved genus-$g$ deformation, where the seed is
transplanted to higher-genus curves and curvature from the Hodge
bundle enters, is developed in Chapter~\ref{chap:higher-genus}.

\smallskip
\noindent\textit{Notation.}
Throughout this chapter, the unadorned differential $d$ on the bar complex denotes the genus-$0$ collision differential $\dzero$ of Convention~\ref{conv:higher-genus-differentials}; it satisfies $\dzero^2 = 0$ (Theorem~\ref{thm:bar-nilpotency-complete}).  The fiberwise curved differential $\dfib$ and the total corrected differential $\Dg{g}$ appear only in Chapter~\ref{chap:higher-genus}.

\medskip

\begin{convention}[Set notation and ordering]\label{conv:set-notation}
Throughout this chapter: collision divisors are $D_{ij}$ with $i < j$ (indices in increasing order); the hat notation $\widehat{ij}$ denotes \emph{omission} of both factors $\phi_i$ and $\phi_j$ after applying the OPE (we write $\widehat{ij}$ for the collision pattern itself, and $\widehat{\phi_i, \phi_j}$ when listing omitted terms in a tensor product).
\end{convention}

\begin{convention}[Bar coalgebra and Koszul dual algebra]
\label{conv:bar-coalgebra-identity}
\index{bar construction!as Koszul dual coalgebra|textbf}
\index{Koszul dual!coalgebra vs.\ algebra|textbf}
The bar construction $\barB_X(\cA)$ of an augmented chiral
algebra~$\cA$ is a dg factorization \emph{coalgebra} on
$\operatorname{Ran}(X)$.  It is the Koszul dual \emph{coalgebra}
of~$\cA$: the bar complex is not a tool for computing the dual,
it \emph{is} the dual.

When $\cA$ is Koszul, the bar coalgebra has cohomology concentrated
in bar degree~$1$.  The Koszul dual \emph{algebra}~$\cA^!$ is a
separate object: it has generators $\mathcal{V}^\vee =
\mathcal{H}om_{\mathcal{O}_X}(\mathcal{V}, \omega_X)$
($\mathcal{D}_X$-module dual of the generators of~$\cA$) and
relations~$R^\perp$ (orthogonal complement under the residue
pairing).  In the classical setting (algebras on a point),
$\cA^!$ is the graded linear dual of the concentrated bar
coalgebra.  In the chiral setting, $\cA^!$ is characterized by
Theorem~A (Theorem~\ref{thm:bar-cobar-isomorphism-main}):
Verdier duality on $\operatorname{Ran}(X)$ intertwines the bar
\emph{coalgebras},
\[
\mathbb{D}_{\operatorname{Ran}}\, \barB_X(\cA)
\;\simeq\; \barB_X(\cA^!),
\]
and the cobar--bar counit
$\Omega_X(\barB_X(\cA)) \xrightarrow{\sim} \cA$
(Theorem~\ref{thm:bar-cobar-inversion-qi})
is a \emph{resolution} of~$\cA$: the cobar of the bar coalgebra
recovers~$\cA$ itself, not its dual.

The bar-dual identity has a precise witness: the \emph{canonical
twisting morphism}
$\tau \colon \barB_X(\cA) \to \cA$,
the degree-$+1$ map projecting bar generators to their algebra
images.  The graded vector space
$\mathfrak{g}_\tau := \Hom(\barB_X(\cA),\, \cA)$ carries a
natural dg Lie structure---the \emph{convolution Lie algebra}---whose
bracket is $[f, g] = \mu_\cA \circ (f \otimes g) \circ
\Delta_{\barB}$ and whose differential is
$\partial f = d_\cA \circ f - (-1)^{|f|} f \circ d_{\barB}$.
The twisting morphism~$\tau$ is a \emph{Maurer--Cartan element}
of this Lie algebra:
\[
\partial\tau + \tfrac{1}{2}[\tau, \tau] = 0
\qquad
\bigl(\text{equivalently: } \partial\tau + \tau \star \tau = 0\bigr),
\]
and the bar-cobar adjunction is the pair
$(\varepsilon_\tau,\, \eta_\tau)$ it determines.
At higher genus, $\tau$ extends to a curved MC element
$\tau_{\mathrm{mod}} = \tau + \Theta_\cA$
in the modular convolution algebra
$\mathfrak{g}_\tau \widehat{\otimes} R\Gamma(\overline{\mathcal{M}}_{g,\bullet})$
(Remark~\ref{rem:theta-modular-twisting}), whose curvature
$\kappa(\cA)\cdot\omega_g$ controls the genus tower.
The four main theorems are four properties of~$\tau$:
existence~(A), invertibility~(B), branch structure~(C),
leading coefficient~(D).

\smallskip\noindent
In summary:
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lll}
\textbf{Object} & \textbf{Type} & \textbf{Relationship} \\
\hline
$\barB_X(\cA)$ & factorization coalgebra
  & the Koszul dual coalgebra \\[2pt]
$\cA^!$ & chiral algebra
  & generators $= \mathcal{V}^\vee$,
    relations $= R^\perp$ \\[2pt]
$\mathbb{D}_{\operatorname{Ran}}\barB_X(\cA)$
  & factorization coalgebra
  & $\simeq \barB_X(\cA^!)$ (Theorem~A) \\[2pt]
$\Omega_X(\barB_X(\cA))$ & chiral algebra
  & $\simeq \cA$ (resolution, not $\cA^!$)
\end{tabular}
\end{center}
\end{convention}

\begin{convention}[Chiral product vs.\ chiral bracket]
\label{conv:product-vs-bracket}
\index{chiral product|textbf}
\index{chiral bracket|textbf}
The \emph{chiral product}
$\mu \colon j_* j^*(\cA \boxtimes \cA) \to \Delta_!(\cA)$
(Definition~\ref{def:chiral-algebra}) encodes all OPE pole
orders simultaneously.  The \emph{chiral bracket}
$\{a,b\} = a_{(0)}b$ extracts the simple-pole residue of~$\mu$;
the \emph{invariant pairing} $\kappa(a,b) = a_{(1)}b$ extracts
the double-pole residue.  The bar differential
$d_{\mathrm{res}}$ uses the full product~$\mu$
(Proposition~\ref{prop:pole-decomposition}), which decomposes as
$d_{\mathrm{res}} = d_{\mathrm{bracket}} + d_{\mathrm{curvature}}$:
the bracket component uses $\{,\}$; the curvature component
uses~$\kappa$.  Neither component is individually a differential
(\S\ref{sec:selection-principle}).
\end{convention}

\label{rem:bar-cobar-hms}%

\begin{remark}[Fourier seed computations]\label{rem:bar-cobar-fourier-seed}
The reader who has worked through the Fourier seed computations
(Chapter~\ref{ch:fourier-seed}) has already seen the bar differential
extract OPE coefficients via residues against the logarithmic
propagator.  We now develop the general construction.
\end{remark}

\section{The geometric bar complex}
\label{sec:bar-cobar}

\subsection{OPE coefficients as residues}

\begin{remark}[Physical origin]\label{rem:physical-genesis}
In 2D conformal field theory, the operator product expansion (OPE)
\[\phi_i(z)\phi_j(w) = \sum_{k} \frac{C_{ij}^k}{(z-w)^{h_i+h_j-h_k}} \phi_k(w) + \text{(less singular)}\]
encodes the structure constants $C_{ij}^k$ (fusion rules) and conformal weights $h_i$ of the theory; associativity of multiple OPEs constrains the $C_{ij}^k$.
The bar construction geometrizes this: $\overline{C}_n(X)$ parametrizes insertion points, $D_{ij}$ encodes the limit $z_i \to z_j$, $\eta_{ij} = d\log(z_i - z_j)$ carries the singularities, and $\operatorname{Res}_{D_{ij}}$ extracts the OPE coefficients.
\end{remark}

\begin{remark}[Parallel track: the BV complex]\label{rem:bv-parallel-track}
\index{BV complex!parallel track}
The bar complex developed in this chapter has a second life as the
BV complex of a chiral field theory.  In the BV formalism
(Costello--Gwilliam~\cite{CG17}), a chiral algebra~$\cA$ determines a
classical field theory whose fields are generators of~$\cA$ and whose
\emph{antifields} are cogenerators of~$\cA^!$; the BV bracket arises from
the residue pairing on configuration spaces.  The identification
\[
\text{bar complex of } \cA
\;=\; \text{BV complex of the chiral field theory of } \cA
\]
is made precise in Theorem~\ref{thm:brst-bar-genus0}.  The reader
may therefore read each construction in this chapter with dual vision:

\begin{center}
\small
\begin{tabular}{ll}
\textbf{This chapter} & \textbf{BV reading} \\ \hline
Bar differential $d_{\mathrm{res}}$ & BRST operator \\
Logarithmic form $\eta_{ij}$ & Propagator \\
Arnold relation $\Rightarrow d^2 = 0$ & Quantum master equation \\
Bar cohomology $H^*(\bar{B}(\cA))$ & Physical observables \\
Curvature $m_0$ (Chapter~\ref{chap:higher-genus}) & Conformal anomaly
\end{tabular}
\end{center}
\noindent
This parallel track is not an analogy; it is a theorem
(Chapter~\ref{ch:bv-brst}).  We develop the algebraic-geometric
side first because it is the side that admits complete proofs.
\end{remark}

\begin{example}[OPE as residue: the Heisenberg current]\label{ex:ope-to-residue}
The Heisenberg current $J(z)$ with OPE $J(z)J(w) = k/(z-w)^2 + \text{reg.}$ gives the bar element $J(z_1) \otimes J(z_2) \otimes \eta_{12} \in \bar{B}^2(\mathcal{H})$, where $\eta_{12} = d\log(z_1 - z_2)$.  The bar differential extracts a residue: setting $\epsilon = z_1 - z_2$, the OPE double pole combined with $\eta_{12}$ produces $\operatorname{Res}_{\epsilon=0}[\epsilon^{-3}d\epsilon] = 0$ (triple pole, no residue).  The central charge $k$ is invisible at genus~$0$; it appears at genus~$1$ as the curvature $m_0$ (Example~\ref{ex:heisenberg-d-deg1}).
\end{example}

\begin{remark}[Logarithmic forms are forced]\label{rem:why-log-forced}
Logarithmic forms $\eta_{ij} = d\log(z_i - z_j)$ are distinguished among meromorphic 1-forms with poles along diagonals by three requirements, which together determine them uniquely.

\emph{Conformal invariance.}
Under a conformal transformation $z \mapsto f(z)$, a direct computation gives
$d\log(f(z_i) - f(z_j)) = \frac{f'(z_i)dz_i - f'(z_j)dz_j}{f(z_i) - f(z_j)}$,
which near the diagonal $z_i \approx z_j$ reduces to $(dz_i - dz_j)/(z_i - z_j)$
by cancellation of $f'$.  Thus $\eta_{ij}$ is conformally invariant up to regular terms.

\emph{Well-defined residues.}
The residue $\operatorname{Res}_{D_{ij}}$ requires a \emph{simple pole} along $D_{ij}$: forms with higher-order poles (e.g.\ $dz_i/(z_i - z_j)^2$) do not admit canonical residues.  A logarithmic form $\omega = \frac{df}{f} \wedge \alpha + \beta$ with $f = z_i - z_j$ has $\operatorname{Res}_{D_{ij}}(\omega) = \alpha|_{D_{ij}}$, which is canonical.

\emph{Arnold relations.}
The cyclic identity
$\eta_{ij} \wedge \eta_{jk} + \eta_{jk} \wedge \eta_{ki} + \eta_{ki} \wedge \eta_{ij} = 0$
is the form-level expression of $d^2 = 0$ on configuration spaces; it holds for $d\log$ forms and fails for other meromorphic 1-forms with simple poles.

Logarithmic forms are therefore the unique solution to the constraints of conformal invariance, canonical residues, and differential nilpotence.
\end{remark}

\subsection{Non-abelian Poincaré perspective on bar construction}

\begin{definition}[Bar as factorization homology]\label{def:bar-fh}
The geometric bar construction is factorization homology of the
chiral algebra, following the Beilinson--Drinfeld factorization
framework~\cite[\S3.4]{BD04}:
\[\bar{B}^{\text{geom}}_n(\mathcal{A}) = \int_{\overline{C}_{n+1}(X)/X} \mathcal{A}\]
where we integrate over configuration spaces relative to $X$.
\end{definition}

\begin{remark}[Configuration spaces]\label{rem:why-config-NAP}
In non-abelian Poincar\'e duality~\cite[\S3.4]{BD04}, one integrates
over configuration spaces rather than the manifold itself.  The
compactification $\overline{C}_n(X)$ adds boundary divisors encoding
collision data; the key inputs are~\cite[Theorem~3.4.22, \S3.6]{BD04}
(Ran space as the correct geometric setting).  Residue extraction is
the NAP analogue of the cup product.
\end{remark}

\begin{theorem}[Bar construction as NAP homology; \ClaimStatusProvedHere]\label{thm:bar-NAP-homology}\label{thm:bar-computes-chiral-homology}
\index{factorization homology!via bar complex}
Let $\mathcal{A}$ be a chiral algebra on a smooth curve $X$ satisfying:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Holonomicity}: $\mathcal{A}$ is a holonomic
  $\mathcal{D}_X$-module (equivalently, locally finitely generated
  with regular singularities).  Concretely, the solution space of the
  $\mathcal{D}_X$-equations on any disk is finite-dimensional---the
  algebraic counterpart of finite-dimensional state spaces at each
  point.
\item \emph{Excision}: the factorization algebra associated
  to~$\mathcal{A}$ satisfies the Weiss cosheaf condition
  (Definition~\ref{def:weiss-cover}), i.e., the
  factorization structure glues over Weiss covers.  This
  provides the descent data for factorization homology.
\end{enumerate}
Then the geometric bar complex computes factorization homology:
\[H_*(\bar{B}^{\text{geom}}(\mathcal{A})) \cong \int_{C_*(X)} \mathcal{A}\]

This is factorization homology of $X$ with coefficients in $\mathcal{A}$ in the sense of Ayala--Francis~\cite{AF15}.  Holonomicity guarantees finite-dimensionality of stalks, which is needed for the Ayala--Francis identification~\cite[Theorem~5.1]{AF15}; excision provides the descent data.

The coalgebra structure on $\bar{B}^{\text{geom}}(\mathcal{A})$ arises from the coproduct in factorization homology:
\[\int_X A \to \int_{X_1} A \otimes \int_{X_2} A\]
when X decomposes as $X = X_1 \sqcup X_2$.
\end{theorem}

\begin{proof}
The identification follows from \cite{AF15} (for the factorization homology framework) and \cite{BD04} (Section~3.4, for the chiral algebra case).  The bar differential $d = d_{\text{int}} + d_{\text{res}} + d_{dR}$ corresponds to the three components of the factorization structure:
\begin{itemize}
\item $d_{\text{int}}$: Internal operations in $\mathcal{A}$ (factorization algebra structure)
\item $d_{\text{res}}$: Residues at collisions (the chiral bracket, realizing the NAP cup product)
\item $d_{dR}$: de Rham differential on logarithmic forms
\end{itemize}
The key verification is that Weiss covers of $C_n(X)$ compute factorization homology (\cite{AF15}, Theorem~5.1), and the FM compactification provides a canonical system of Weiss covers whose \v{C}ech complex is precisely the bar complex (Definition~\ref{def:weiss-cover}).
\end{proof}

With the bar and cobar constructions in hand, we can articulate the organizing principle of this monograph.

\begin{remark}[The nilpotence-periodicity correspondence]
\label{rem:nilpotence-periodicity}
\index{nilpotence-periodicity correspondence|textbf}
\index{periodicity!as exponential of nilpotence}
The logarithmic form~$\eta_{ij} = d\log(z_i - z_j)$ is not an
incidental choice of kernel: the bar construction is the
\emph{categorical logarithm} for chiral algebras, mapping
multiplicative structure (the OPE) to additive/nilpotent structure
(the bar differential with $\dzero^2 = 0$).  The cobar construction
is the corresponding \emph{exponential}, reconstructing the algebra
from the nilpotent data.  The structural principle governing the
entire theory is:
\begin{center}
\emph{Nilpotence is the logarithm of periodicity.}
\end{center}
At genus~$0$, the logarithm~$\eta_{ij}$ is single-valued
on~$C_2(\mathbb{P}^1)$, the bar differential is nilpotent
($\dzero^2 = 0$), and the monodromy is trivial.  At
genus~$g \geq 1$, the logarithm $d\log E(z_i,z_j)$ acquires
monodromy around the $B$-cycles of~$\Sigma_g$, the fiberwise bar
differential fails nilpotence by
$\dfib^{\,2} = \kappa(\cA)\cdot\omega_g$, and the curvature
$\kappa(\cA)$ is the \emph{infinitesimal generator} of this
monodromy---the residue at the branch point of the logarithm.
This is the chiral Riemann--Hilbert correspondence: the nilpotent
datum~$\kappa$ determines the periodic datum (the monodromy of the
bar family over~$\overline{\mathcal{M}}_g$) via exponentiation.

The four theorems are four aspects of this correspondence:
Theorem~A asserts that the categorical logarithm and exponential
exist; Theorem~B that they are mutually inverse on the
convergence domain (the Koszul locus); Theorem~C that the failure
off the convergence domain decomposes into complementary
Lagrangians (the branch structure of the logarithm); and
Theorem~D that the leading coefficient~$\kappa(\cA)$ of the
logarithm determines the full scalar package.

The modular periodicity profile~$\Pi(\cA)$ is the
global/exponential counterpart of the infinitesimal/nilpotent
characteristic~$\kappa(\cA)$.  At the scalar level, the T-matrix
eigenvalues $\lambda = \exp(2\pi i(h - c/24))$ are the
\emph{exponentials} of conformal weights shifted by the central
charge; the modular period~$N$ is the smallest positive integer for
which $\exp(2\pi i N c/24) = 1$.  At the geometric level, the
nilpotency $\kappa(\lambda)^{g-1} = 0$
(Theorem~\ref{thm:geometric-depth-smooth}) makes the operator
$\exp(\kappa(\lambda))$ \emph{unipotent}, not periodic: geometry
provides a stabilization threshold, not a period.  True periodicity
arises from modular and quantum sources whose nilpotent generators
have finite-order exponentials.
\end{remark}

\subsection{Precise construction of the bar complex}

\begin{definition}[Genus-graded geometric bar complex]
The bar complex at genus $g$ is:
\[\bar{B}^{(g),n}(\mathcal{A}) = \Gamma\left(\overline{C}_{n+1}^{(g)}(\Sigma_g), j_*j^*\mathcal{A}^{\boxtimes(n+1)} \otimes \Omega^n(\log D^{(g)})\right)\]

The total bar complex is:
\[\bar{B}(\mathcal{A}) = \bigoplus_{g=0}^{\infty} \bar{B}^{(g)}(\mathcal{A})\]
\end{definition}

\begin{convention}[Global sections vs.\ derived global sections]\label{conv:gamma-vs-rgamma}
\index{global sections!underived vs.\ derived}
Throughout this chapter, $\Gamma(-)$ denotes \emph{underived} global sections:
for a sheaf $\mathcal{F}$ on a variety $Y$, the symbol $\Gamma(Y, \mathcal{F})$
is the vector space $H^0(Y, \mathcal{F})$.  When derived global sections are
needed (e.g., over moduli stacks or in derived $\mathcal{D}$-module arguments),
we write $R\Gamma$ explicitly.  In particular, the bar complex definition above
uses honest global sections of a coherent sheaf on the smooth variety
$\overline{C}_{n+1}^{(g)}(\Sigma_g)$.
\end{convention}

\begin{remark}[Components of the definition]\label{rem:unpacking-bar-def}
The FM compactification $\overline{C}_{n+1}^{(g)}(\Sigma_g)$ parametrizes $(n+1)$ points on $\Sigma_g$ with collision patterns (Chapter~\ref{chap:config-spaces}).  The degree-$n$ bar complex has $(n+1)$ insertions $\phi_0(z_0) \otimes \cdots \otimes \phi_n(z_n)$, where $\phi_0$ is the ``output'' (operadic structure).

The external tensor product $j_*j^*\mathcal{A}^{\boxtimes(n+1)}$ extends $\mathcal{A}^{\boxtimes(n+1)}$ from the open locus of distinct points across collisions, with the OPE controlling the singularity structure (BD~\cite[\S3.4.14--3.4.22]{BD04}).

The logarithmic forms $\Omega^n(\log D^{(g)})$ are spanned at genus~$0$ by wedge products of $\eta_{ij} = d\log(z_i - z_j)$; at genus $g \geq 1$, theta functions ($g=1$) and prime forms ($g \geq 2$) contribute.

A global section $\alpha \in \bar{B}^{(g),n}(\mathcal{A})$ is a ``correlation function'':
\[\alpha = \sum_I a_I(z_0, \ldots, z_n) \cdot \phi_{i_0}(z_0) \otimes \cdots \otimes \phi_{i_n}(z_n) \otimes \omega_I(z_0, \ldots, z_n)\]
the geometric incarnation of an $(n+1)$-point function.
\end{remark}

\begin{example}[Genus zero, degree 1]\label{ex:bar-genus0-deg1}
At genus 0, degree 1:
\[\bar{B}^{(0),1}(\mathcal{A}) = \Gamma\left(\overline{C}_2(\mathbb{P}^1), j_*j^*(\mathcal{A} \boxtimes \mathcal{A}) \otimes \Omega^1(\log D_{12})\right)\]

\emph{Configuration space.} $C_2(\mathbb{P}^1) \subset (\mathbb{P}^1)^2$ has $\dim_\mathbb{C} = 2$.  The $\text{PSL}_2$ action is transitive on ordered pairs of distinct points, so the quotient $C_2(\mathbb{P}^1)/\text{PSL}_2$ is a point.  After fixing the $\text{PSL}_2$ gauge (e.g., $z_2 = \infty$), the residual coordinate is $z_1 \in \mathbb{C}$.

\emph{Boundary divisor.} $D_{12} = \{z_1 = z_2\}$ is a single point in $\overline{C}_2(\mathbb{P}^1)$.

\emph{Logarithmic 1-forms.} $\Omega^1(\log D_{12})$ consists of forms:
\[\omega = f(z_1, z_2) \cdot \eta_{12}\]
where $\eta_{12} = \frac{dz_1 - dz_2}{z_1 - z_2}$ and $f$ is a meromorphic function.

\emph{Elements.} Typical element is:
\[\phi_i(z_1) \otimes \phi_j(z_2) \otimes \eta_{12}\]

\emph{Dimension.} If $\mathcal{A}$ has $N$ generators, then:
\[\dim \bar{B}^{(0),1}(\mathcal{A}) = N^2 \cdot \dim H^0(\overline{C}_2(\mathbb{P}^1), \Omega^1(\log D_{12}))\]

For $\mathbb{P}^1$, $\dim H^0(\overline{C}_2, \Omega^1(\log D)) = 1$ (only constant coefficient functions after fixing $\text{PSL}_2$).

Hence $\dim \bar{B}^{(0),1}(\mathcal{A}) = N^2$.
\end{example}

\begin{example}[Genus zero, degree 2]\label{ex:bar-genus0-deg2}
At genus 0, degree 2:
\[\bar{B}^{(0),2}(\mathcal{A}) = \Gamma\left(\overline{C}_3(\mathbb{P}^1), j_*j^*(\mathcal{A}^{\boxtimes 3}) \otimes \Omega^2(\log D)\right)\]

\emph{Configuration space.} $\overline{C}_3(\mathbb{P}^1)$ has $\dim_\mathbb{C} = 3$.  Fixing the $\text{PSL}_2$ gauge (e.g., $z_3 = 0, z_2 = 1, z_1 = \infty$ for the normalization), the quotient $\overline{C}_3(\mathbb{P}^1)/\text{PSL}_2 \cong \overline{\mathcal{M}}_{0,4} \cong \mathbb{P}^1$ has $\dim_\mathbb{C} = 1$.  The $\text{PSL}_2$-reduced configuration has one free cross-ratio parameter.

\emph{Boundary divisor.} $D = D_{12} \cup D_{23} \cup D_{13}$ (three divisors, one for each pair of points colliding).

\emph{Logarithmic 2-forms.} $\Omega^2(\log D)$ is spanned by:
\[\eta_{12} \wedge \eta_{23}, \quad \eta_{23} \wedge \eta_{31}, \quad \eta_{31} \wedge \eta_{12}\]
subject to Arnold relation:
\[\eta_{12} \wedge \eta_{23} + \eta_{23} \wedge \eta_{31} + \eta_{31} \wedge \eta_{12} = 0\]

So the space of 2-forms is 2-dimensional (three generators, one relation).

\emph{Elements.} Typical element is:
\[\sum_{i,j,k} c_{ijk} \cdot \phi_i(z_1) \otimes \phi_j(z_2) \otimes \phi_k(z_3) \otimes (\eta_{12} \wedge \eta_{23})\]

\emph{Dimension.} 
\[\dim \bar{B}^{(0),2}(\mathcal{A}) = N^3 \cdot 2\]

This grows rapidly with $n$.
\end{example}

\subsubsection{The bar differential}

\begin{definition}[Bar differential]\label{def:bar-differential-complete}%
\label{def:geometric-bar}\label{def:geometric-bar-definition}\label{def:bar-geometric}%
\label{def:bar-diff-detailed}\label{def:diff-total}%
\index{bar complex!differential|textbf}
The differential $d: \bar{B}^n(\mathcal{A}) \to \bar{B}^{n+1}(\mathcal{A})$ has three components (in the cohomological grading convention $|d|=+1$; the residue component collapses two tensor factors, decreasing the tensor arity by one, while simultaneously increasing the form degree, so that the net cohomological degree is $+1$):
\[d = d_{\text{internal}} + d_{\text{residue}} + d_{\text{form}}\]

\emph{Component 1: Internal differential $d_{\text{internal}}$.}

If $\mathcal{A}$ has an internal differential $d_\mathcal{A}: \mathcal{A} \to \mathcal{A}$ (e.g., from a BRST complex or de Rham differential), we apply it to each tensor factor:
\[d_{\text{internal}}\left(\phi_0 \otimes \cdots \otimes \phi_n \otimes \omega\right) = \sum_{i=0}^n (-1)^{\epsilon_i} \left(\phi_0 \otimes \cdots \otimes d_\mathcal{A}(\phi_i) \otimes \cdots \otimes \phi_n \otimes \omega\right)\]
where $\epsilon_i$ is the Koszul sign:
\[\epsilon_i = \sum_{j=0}^{i-1} |\phi_j| + \sum_{j=0}^{i-1} 1 = \text{(total degree before } \phi_i\text{)}\]

\emph{Component 2: Residue differential $d_{\text{residue}}$.}

The main geometric operation extracts OPE coefficients via residues at collision divisors.
\[d_{\text{residue}}\left(\phi_0 \otimes \cdots \otimes \phi_n \otimes \omega\right) = \sum_{0 \leq i < j \leq n} (-1)^{\sigma_{ij}} \text{Res}_{D_{ij}}\left[\mu(\phi_i, \phi_j) \otimes \text{(other factors)} \otimes \omega\right]\]
where:
\begin{itemize}
\item $\mu: \mathcal{A} \otimes \mathcal{A} \to \mathcal{A}$ is the OPE (chiral product)
\item $D_{ij} \subset \overline{C}_{n+1}(\Sigma_g)$ is the divisor where $z_i = z_j$
\item $\text{Res}_{D_{ij}}$ is the residue along $D_{ij}$ (see \S\ref{sec:residue-calculus} below)
\item $\sigma_{ij}$ is a sign determined by:
  \begin{enumerate}
  \item Position of $i,j$ in the tensor product (Koszul sign)
  \item Orientation of $D_{ij}$ as boundary (geometric sign)
  \item Grading of fields $\phi_i, \phi_j$ (super sign)
  \end{enumerate}
\end{itemize}

The explicit formula for the sign is:
\[\sigma_{ij} = \left(\sum_{k=0}^{i-1} |\phi_k|\right) + \left(\sum_{k=i+1}^{j-1} |\phi_k|\right) + |\phi_i| + \epsilon_{\text{geom}}(D_{ij})\]
where $\epsilon_{\text{geom}}(D_{ij}) = 0$ or $1$ depending on orientation convention (see Convention \ref{conv:orientations-enhanced}).

\emph{Component 3: Form differential $d_{\text{form}}$.}

Apply the de Rham differential to the form component:
\[d_{\text{form}}\left(\phi_0 \otimes \cdots \otimes \phi_n \otimes \omega\right) = (-1)^{\sum_{i=0}^n |\phi_i|} \left(\phi_0 \otimes \cdots \otimes \phi_n \otimes d_{\text{dR}}(\omega)\right)\]
where $d_{\text{dR}}: \Omega^n \to \Omega^{n+1}$ is the de Rham differential on forms.

\end{definition}

\begin{remark}[Three components]\label{rem:three-components}
\index{boundary divisor!in bar differential}
The component $d_{\text{internal}}$ encodes the differential on $\mathcal{A}$ (BRST symmetry); $d_{\text{residue}}$ extracts OPE data via residues at $D_{ij}$; $d_{\text{form}}$ is the de Rham differential on configuration space (Ward identities).

Nilpotency $d^2 = 0$ is \emph{not} automatic and requires the Borcherds identity ($d_{\text{residue}}^2 = 0$; Jacobi alone is insufficient---Proposition~\ref{prop:pole-decomposition}), Stokes' theorem ($\{d_{\text{form}}, d_{\text{residue}}\} = 0$), and the derivation property ($d_{\text{internal}}$ commutes with both).
\end{remark}

\begin{example}[Heisenberg degree-\texorpdfstring{$1$}{1} bar differential]\label{ex:heisenberg-d-deg1}
\label{ex:free-boson-d-deg1}
The Heisenberg algebra $\mathcal{H}_k$ with OPE $J(z)J(w) = k/(z-w)^2 + \text{regular}$ has
vanishing bar differential on $\alpha = J \otimes J \otimes \eta_{12} \in \bar{B}^1$: the OPE combined with $\eta_{12}$ produces a triple pole $\epsilon^{-3}\,d\epsilon$, whose residue is zero.  The element $\alpha$ is a non-trivial cocycle.  The level $k$ is invisible at genus $0$ and appears only as a genus-$1$ quantum correction.  See Chapter~\ref{ch:heisenberg-frame}, \S\ref{sec:frame-bar-deg1} for the full computation.
\end{example}

\begin{definition}[Orientation bundle across genera]
For the configuration space $C_{p+1}^{(g)}(\Sigma_g)$, the orientation bundle includes genus-dependent factors:

\[\text{or}_{p+1}^{(g)} = \det(TC_{p+1}^{(g)}(\Sigma_g)) \otimes \text{sgn}_{p+1} \otimes \mathcal{L}_g\]

where:
\begin{enumerate}
\item $\det(TC_{p+1}^{(g)}(\Sigma_g))$ is the top exterior power of the tangent bundle
\item $\text{sgn}_{p+1}$ is the sign representation of $S_{p+1}$
\item $\mathcal{L}_g$ encodes the genus-dependent orientation from the period matrix
\end{enumerate}

This ensures $d^2 = 0$ with consistent signs across all face maps, compatibility with $\mathfrak{S}_{p+1}$, correct genus-graded $A_\infty$ signs, and $\text{Sp}(2g, \mathbb{Z})$-covariance.
\end{definition}

\begin{remark}[Orientation convention]
We fix orientations at each genus by complexifying the orientation sheaf of the real blow-up $\widetilde{C}_{p+1}^{(g)}(\mathbb{R})$, tensoring with $\text{sgn}_{p+1}$ so that $\sigma^* \text{or}_{p+1}^{(g)} = \text{sign}(\sigma) \cdot \text{or}_{p+1}^{(g)}$ for $\sigma \in S_{p+1}$, and at genus $g \geq 1$ including the period matrix orientation $\mathcal{L}_g$.
\end{remark}

\subsection{Sign conventions}\label{sec:sign-conventions}

\begin{convention}[Enhanced sign system]\label{conv:orientations-enhanced}
The bar complex requires three types of sign conventions:

\emph{Type 1: Koszul signs (algebraic).}

The standard Koszul sign rule (Appendix~\ref{app:sign-conventions}, \S\ref{sec:sign-dictionary-complete}) applies with total degree $|\phi| + k$ for a field $\phi \in \mathcal{A}$ tensored with a form in $\Omega^k$.

\emph{Type 2: Orientation signs (geometric).}

Configuration spaces and their boundary divisors carry orientations:

\begin{enumerate}
\item \emph{Configuration space orientation:} $\overline{C}_{n+1}(\Sigma_g)$ is oriented via the complex structure:
\[\text{or}(\overline{C}_{n+1}) = dz_1 \wedge d\bar{z}_1 \wedge \cdots \wedge dz_n \wedge d\bar{z}_n\]
(after modding out by automorphisms; see \S\ref{sec:sign-conventions} below)

\item \emph{Divisor orientation:} Each boundary divisor $D_{ij}$ is oriented by the \emph{outward normal} convention:
\[\text{or}(D_{ij}) = d\epsilon_{ij} \wedge \text{or}(\text{tangent to } D_{ij})\]
where $\epsilon_{ij} = |z_i - z_j|$ points outward (into the interior).

\item \emph{Codimension-2 strata:} At intersections $D_{ij} \cap D_{jk} = D_{ijk}$:
\[\text{or}(D_{ijk}) = d\epsilon_{ij} \wedge d\epsilon_{jk} \wedge \text{or}(\text{tangent})\]

The key identity (Lemma~\ref{lem:orientation}, item~(3)):
\[\text{or}(D_{ijk})|_{D_{ij}} = -\text{or}(D_{ijk})|_{D_{jk}}\]
This sign difference ensures Stokes' theorem holds with correct cancellations.

\item \emph{Residue orientation:} When computing $\text{Res}_{D_{ij}}$, we use:
\[\text{Res}_{D_{ij}}\left(\frac{d\epsilon_{ij}}{\epsilon_{ij}} \wedge \alpha\right) = (+1) \cdot \alpha|_{D_{ij}}\]
(no extra sign for residue extraction)
\end{enumerate}

\emph{Type 3: Operadic signs.}

The bar complex has an operadic structure (composition of operations). When composing two operations, the sign arises from three sources: \emph{grafting trees} (reordering edges when attaching one tree to another), \emph{shuffle signs} (permuting tensor factors to bring colliding fields together), and the \emph{Koszul sign} (moving differential forms past fields).

The formula (for operads): if we compose operations of arity $m$ and $n$ at the $i$-th input:
\[\text{sign} = (-1)^{\epsilon}\]
where:
\[\epsilon = \sum_{j=1}^{i-1} |p_j| \cdot |q|\]
($|p_j|$ are degrees of inputs before position $i$, $|q|$ is degree of the composed operation)

\emph{Compatibility condition.}

These three types of signs must be compatible to ensure $d^2 = 0$. The key relations are:

\begin{enumerate}
\item \emph{Koszul-Orientation compatibility:}
\[\text{sign}_{\text{Koszul}}(\phi_i \leftrightarrow \phi_j) \cdot \text{sign}_{\text{orient}}(D_{ij} \leftrightarrow D_{ji}) = (-1)^{1}\]
(fields anticommute up to orientation sign)

\item \emph{Orientation-Residue compatibility:}
\[\text{Res}_{D_{ij}} \circ \text{Res}_{D_{jk}} + \text{Res}_{D_{jk}} \circ \text{Res}_{D_{ij}} = 0 \quad \text{(with correct signs)}\]
(residues anticommute at codimension-2 strata)

\item \emph{Koszul-Operadic compatibility:}
\[\text{sign}_{\text{Koszul}}(\text{reorder}) = \text{sign}_{\text{operadic}}(\text{compose})\]
(both give the same sign for the same operation)
\end{enumerate}

\end{convention}

\begin{lemma}[Sign compatibility; \ClaimStatusProvedHere]\label{lem:sign-compatibility}
The three types of signs (Koszul, orientation, operadic) are mutually compatible in the sense required for $d^2 = 0$.
\end{lemma}

\begin{proof}
We verify each compatibility relation:

\emph{Relation 1: Koszul-Orientation.}

Consider swapping two fields $\phi_i \otimes \phi_j \to \phi_j \otimes \phi_i$:
- Koszul sign: $(-1)^{|\phi_i| \cdot |\phi_j|}$
- This corresponds to swapping collision divisors $D_{ij} \leftrightarrow D_{ji}$
- Orientation sign: $\text{or}(D_{ji}) = -\text{or}(D_{ij})$ (from antisymmetry of differentials)

The product:
\[(-1)^{|\phi_i| \cdot |\phi_j|} \cdot (-1) = (-1)^{|\phi_i| \cdot |\phi_j| + 1}\]

For bosonic fields ($|\phi_i|, |\phi_j|$ even), this is $(-1)^{0+1} = -1$.
For fermionic fields ($|\phi_i|, |\phi_j|$ odd), this is $(-1)^{1+1} = +1$.

This yields the correct commutation and anticommutation relations for super-objects.

\emph{Relation 2: Orientation-Residue.}

At a codimension-2 stratum $D_{ijk} = D_{ij} \cap D_{jk}$:

Approach from $D_{ij}$ side:
\[\text{or}(D_{ijk})|_{D_{ij}} = d\epsilon_{jk} \wedge \text{or}(D_{ij})\]

Approach from $D_{jk}$ side:
\[\text{or}(D_{ijk})|_{D_{jk}} = d\epsilon_{ij} \wedge \text{or}(D_{jk})\]

By Lemma~\ref{lem:orientation}(3), these differ by a sign: $\text{or}(D_{ijk})|_{D_{ij}} = -\text{or}(D_{ijk})|_{D_{jk}}$.

Now compute double residue:
\begin{align*}
\text{Res}_{D_{ij}} \text{Res}_{D_{jk}}(\omega) + \text{Res}_{D_{jk}} \text{Res}_{D_{ij}}(\omega) &= \int_{D_{ijk}} \omega|_{D_{ijk}} \text{ (from }\text{or}(D_{ijk})|_{D_{ij}}\text{)} \\
&\quad + \int_{D_{ijk}} \omega|_{D_{ijk}} \text{ (from }\text{or}(D_{ijk})|_{D_{jk}}\text{)} \\
&= (+1) \int + (-1) \int = 0
\end{align*}

The orientations differ by exactly the sign needed for cancellation.

\emph{Relation 3: Koszul-Operadic.}

Consider composing two operations $\mu_1: V_1 \otimes V_2 \to W_1$ and $\mu_2: W_1 \otimes V_3 \to W_2$.

Koszul sign for moving $V_2$ past $W_1$:
\[(-1)^{|V_2| \cdot |W_1|}\]

Operadic sign for grafting:
\[(-1)^{\epsilon}\] where $\epsilon = |V_1| + |V_2|$ (degrees of inputs before the graft point)

These match when we account for the suspension in the bar construction ($W_1$ has degree shifted by 1).  More precisely, the sign convention on the desuspension $s^{-1}\bar{\mathcal{A}}$ is \emph{chosen} so that the Koszul and operadic signs are compatible; we now verify that this choice is consistent.

\emph{General case.}
Let $T$ be the rooted tree labeling the given bar element.  Each of
the three sign sources defines a parity character on $\operatorname{Aut}(T)$:
Koszul signs come from permuting tensor factors, orientation signs
come from permuting configuration-space coordinates, and operadic
signs come from grafting odd inputs through the operad composition.

The key identity is checked on an adjacent transposition of two inputs
$\phi_i,\phi_j$.  On the desuspension $s^{-1}\bar{\mathcal{A}}$, that
transposition contributes
\[
(-1)^{(|\phi_i|-1)(|\phi_j|-1)}
= (-1)^{|\phi_i||\phi_j|}
  (-1)^{|\phi_i|+|\phi_j|}
  (-1).
\]
The first factor is the Koszul sign, the second is the operadic sign,
and the last factor is the orientation sign from swapping the two
coordinates.  Hence the combined action on
$s^{-1}\bar{\mathcal{A}}$ already contains all three sign sources.

Because every tree automorphism is generated by adjacent
transpositions, compatibility for generators implies
\[
\epsilon_{\mathrm{Koszul}} \cdot
\epsilon_{\mathrm{orient}} \cdot
\epsilon_{\mathrm{operad}} = +1
\]
for every rooted tree~$T$.  The arity-$2$ computation above supplies
the base case, and induction on tree depth propagates the identity to
all graftings.
\end{proof}

\subsection{\texorpdfstring{Proof that $d^2 = 0$: nine-term verification}{Proof that d2 = 0: nine-term verification}}\label{sec:bar-nilpotency-nine-terms-complete}\label{sec:bar-nilpotency}

\begin{theorem}[Nilpotency of bar differential; \ClaimStatusProvedHere]\label{thm:bar-nilpotency-complete}
\index{bar differential!nilpotence}
\textup{[Regime: quadratic, genus-$0$
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

The differential $d = d_{\text{internal}} + d_{\text{residue}} + d_{\text{form}}$ on the bar complex satisfies:
\[d^2 = 0\]

More precisely, all nine cross-terms arising from $(d_1 + d_2 + d_3)^2$ cancel.
\end{theorem}

\begin{proof}
Write $d = d_1 + d_2 + d_3$ where $d_1 = d_{\text{int}}$ is the internal differential on $\mathcal{A}$, $d_2 = d_{\text{res}}$ extracts residues at collision divisors, and $d_3 = d_{\text{dR}}$ is the de Rham differential on forms. Expanding $(d_1 + d_2 + d_3)^2$, we obtain six terms (three diagonal and three anticommutators) which we verify separately.

\emph{Diagonal terms.} The identity $d_1^2 = 0$ holds because $d_\mathcal{A}^2 = 0$ on $\mathcal{A}$: diagonal terms vanish by hypothesis, and cross-terms (where $d_1$ hits two different tensor factors $\phi_i$ and $\phi_j$) cancel in pairs by the Koszul sign rule. The identity $d_3^2 = 0$ is the standard relation $d_{\text{dR}}^2 = 0$ for differential forms.

The identity $d_2^2 = 0$ is the most substantial. In the double sum
\[d_2^2 = \sum_{i<j}\sum_{k<\ell} (-1)^{\sigma_{ij} + \sigma_{k\ell}'}\, \text{Res}_{D_{k\ell}} \circ \text{Res}_{D_{ij}},\]
three cases arise according to how the index sets $\{i,j\}$ and $\{k,\ell\}$ overlap.

\emph{Case (i): Disjoint pairs} ($\{i,j\} \cap \{k,\ell\} = \emptyset$). The divisors $D_{ij}$ and $D_{k\ell}$ intersect transversally in $\partial\overline{C}_{n+1}(X)$. Since the divisors are disjoint (no shared indices), the residue operations themselves commute:
\[\text{Res}_{D_{ij}} \circ \text{Res}_{D_{k\ell}} = \text{Res}_{D_{k\ell}} \circ \text{Res}_{D_{ij}}.\]
The cancellation comes from the signed sum in $d_2$: the ordered pairs $(i,j),(k,\ell)$ and $(k,\ell),(i,j)$ contribute with opposite signs $(-1)^{\sigma_{ij}+\sigma_{k\ell}'}$ and $(-1)^{\sigma_{k\ell}+\sigma_{ij}'}$ (Lemma~\ref{lem:sign-compatibility}), and these signs differ by $(-1)$, so the two terms cancel.

\emph{Case (ii): One overlap} (say $j = k$).  This is the case that produced the Arnold relation in the Heisenberg degree-$2$ computation (\S\ref{sec:frame-bar-deg2}): three boundary strata meet at a triple collision, and their contributions cancel cyclically.  In general: the composition approaches the codimension-2 stratum $D_{ij\ell}$ (triple collision). Three terms contribute, corresponding to the three codimension-1 strata meeting $D_{ij\ell}$:
\begin{align*}
&\text{Res}_{D_{j\ell}} \circ \text{Res}_{D_{ij}}\bigl[\mu(\mu(\phi_i, \phi_j), \phi_\ell)\bigr] + \text{Res}_{D_{ij}} \circ \text{Res}_{D_{j\ell}}\bigl[\mu(\phi_i, \mu(\phi_j, \phi_\ell))\bigr] \\
&\qquad + \text{Res}_{D_{i\ell}} \circ \text{Res}_{D_{ij}}\bigl[\mu(\mu(\phi_i, \phi_\ell), \phi_j)\bigr].
\end{align*}
These cancel by the associativity constraint on the chiral product $\mu$---equivalently, by the Borcherds identity for $\mathcal{A}$---which asserts that the sum of these three iterated-residue terms vanishes for any triple of sections.

\emph{Case (iii): Same pair} ($\{i,j\} = \{k,\ell\}$). Since $\text{Res}_{D_{ij}}$ extracts a simple pole along $D_{ij}$, applying it once produces a section regular along $D_{ij}$, and a second application yields zero: $\text{Res}_{D_{ij}}^2 = 0$.

\emph{Mixed terms.} The anticommutator $\{d_1, d_2\} = 0$ follows from the fact that $d_\mathcal{A}$ is a derivation of $\mathcal{A}$. Since $\mu$ is a morphism of $\mathcal{D}_X$-modules, the internal differential commutes with residue extraction: $d_1 \circ \text{Res}_{D_{ij}} = \text{Res}_{D_{ij}} \circ d_1$.

For $\{d_1, d_3\} = 0$: the operators $d_1$ and $d_3$ act on the algebra and form tensor factors respectively. The Koszul sign accompanying $d_3$ includes a factor $(-1)^{\sum_i |\phi_i|}$ from passing the de Rham differential past the algebra elements. After $d_1$ increases one algebra degree by $1$, the sign acquires an extra factor of $(-1)$. Thus $d_3 \circ d_1 = -d_1 \circ d_3$, and the anticommutator vanishes.

For $\{d_2, d_3\} = 0$: this follows from the residue exact sequence for logarithmic forms.  On a normal crossing divisor $D = \bigcup D_{ij} \subset \overline{C}_{n+1}(X)$, the residue map fits into the exact sequence $0 \to \Omega^k \to \Omega^k(\log D) \xrightarrow{\text{Res}} \bigoplus_{D_{ij}} \Omega^{k-1}_{D_{ij}}(\log D') \to 0$, and the de Rham differential is compatible with the residue map: $\text{Res}_{D_{ij}} \circ d_{\text{dR}} = d_{\text{dR}}|_{D_{ij}} \circ \text{Res}_{D_{ij}}$.  Since $d_2$ is a signed sum of residues and $d_3 = d_{\text{dR}}$, they anticommute (with signs from Convention~\ref{conv:orientations-enhanced}).
\end{proof}

\begin{remark}[Sign-level verification]\label{rem:sign-bridge}
For a complete sign-by-sign verification of $d^2 = 0$ at low degrees
(including the explicit computation for degree-3 elements $[a|b|c]$ in a
graded associative algebra), see Verification~\ref{ver:d2-degree3} and
Proposition~\ref{prop:master-sign} in Appendix~\ref{app:signs}.
\end{remark}

\begin{remark}[Synthesis]\label{rem:d-squared-synthesis}\label{rem:geometric-miracle}
The three mechanisms entering the proof of $d^2 = 0$ ---
the Borcherds identity (algebra), Stokes' theorem (topology), and
residue calculus (analysis) --- all arise from the boundary
stratification of $\overline{C}_n(X)$.  For the Heisenberg algebra,
this reduced to the Arnold relation
(\S\ref{sec:frame-bar-deg2}); in general, the factorization structure
on $\operatorname{Ran}(X)$ forces the compatibility
(Beilinson--Drinfeld~\cite{BD04};
see \S\ref{sec:selection-principle} for the selection principle).
\end{remark}

\begin{proposition}[Pole decomposition of the bar differential; \ClaimStatusProvedHere]\label{prop:pole-decomposition}
\index{bar differential!pole decomposition}
\index{bar differential!bracket component}
\index{bar differential!curvature component}
The residue differential $d_{\mathrm{res}}$ decomposes according to OPE pole order:
\begin{equation}\label{eq:pole-decomposition}
d_{\mathrm{res}} = d_{\mathrm{bracket}} + d_{\mathrm{curvature}}
\end{equation}
where $d_{\mathrm{bracket}}$ extracts residues from simple poles (Lie bracket terms $a_{(0)}b$) and $d_{\mathrm{curvature}}$ extracts residues from double poles (metric/level terms $\kappa(a,b)|0\rangle$).

This decomposition has the following properties:
\begin{enumerate}
\item $d_{\mathrm{bracket}}^2 \neq 0$ in general: the obstruction is the Borcherds associator, which involves iterated residues mixing both pole orders.
\item $d_{\mathrm{curvature}}^2 = 0$: double-pole residues produce scalars (vacuum vectors), and a second residue applied to a scalar vanishes.
\item $d_{\mathrm{res}}^2 = d_{\mathrm{bracket}}^2 + \{d_{\mathrm{bracket}}, d_{\mathrm{curvature}}\} + d_{\mathrm{curvature}}^2 = 0$, so the cross-term $\{d_{\mathrm{bracket}}, d_{\mathrm{curvature}}\}$ exactly compensates the failure of $d_{\mathrm{bracket}}^2 = 0$.
\end{enumerate}

In particular, the Lie-bracket Jacobi identity (which would give $d_{\mathrm{bracket}}^2 = 0$ for a Lie algebra) is \emph{insufficient} for nilpotency of the chiral bar differential.  The full Borcherds identity (associativity of the chiral product $\mu$, involving all pole orders simultaneously) is required.
\end{proposition}

\begin{proof}
For a chiral algebra $\cA$ with OPE $a(z)b(w) \sim \sum_{n \geq 0} a_{(n)}b \cdot (z-w)^{-n-1}$, the residue differential at the divisor $D_{ij}$ extracts:
\[
\mathrm{Res}_{D_{ij}}[\mu(\phi_i, \phi_j) \otimes \omega]
  = \mathrm{Res}_{\epsilon=0}\Bigl[\sum_{n \geq 0}
    \frac{(\phi_i)_{(n)}\phi_j}{\epsilon^{n+1}} \otimes \omega\Bigr]
\]
where $\epsilon = z_i - z_j$ is the local coordinate normal to $D_{ij}$.

The simple-pole contribution ($n = 0$) gives:
\[
d_{\mathrm{bracket}}(\cdots) = \sum_{i < j} (-1)^{\sigma_{ij}}
  \mathrm{Res}_{\epsilon=0}\Bigl[\frac{(\phi_i)_{(0)}\phi_j}{\epsilon}
    \otimes \omega\Bigr],
\]
which extracts the Lie bracket $[\phi_i, \phi_j] = (\phi_i)_{(0)}\phi_j$ via the simple-pole residue of $\omega$.

The double-pole contribution ($n = 1$) gives:
\[
d_{\mathrm{curvature}}(\cdots) = \sum_{i < j} (-1)^{\sigma_{ij}}
  \mathrm{Res}_{\epsilon=0}\Bigl[\frac{(\phi_i)_{(1)}\phi_j}{\epsilon^2}
    \otimes \omega\Bigr],
\]
which extracts the invariant bilinear form $(\phi_i)_{(1)}\phi_j = \kappa(\phi_i, \phi_j)|0\rangle$.  For Kac--Moody algebras, this is the level: $(J^a)_{(1)}J^b = k\,\delta^{ab}|0\rangle$.

\emph{Property~(2).}  Since $d_{\mathrm{curvature}}$ replaces a pair $(\phi_i, \phi_j)$ by a scalar multiple of the vacuum $|0\rangle$, the output of $d_{\mathrm{curvature}}$ at position $i$ is proportional to $|0\rangle$.  A subsequent application of $d_{\mathrm{curvature}}$ (or $d_{\mathrm{bracket}}$) involving this vacuum position produces $|0\rangle_{(n)}\phi_k = 0$ for $n \geq 0$, hence $d_{\mathrm{curvature}}^2 = 0$.

\emph{Property~(1).}  In the double sum $d_{\mathrm{bracket}}^2$, the one-overlap terms (Case~(ii) of Theorem~\ref{thm:bar-nilpotency-complete}) produce iterated residues $\mathrm{Res}_{D_{j\ell}}\mathrm{Res}_{D_{ij}}[(\phi_i)_{(0)}(\phi_j)_{(0)}\phi_\ell \otimes \omega]$.  The Borcherds identity for the chiral product asserts:
\begin{equation}\label{eq:borcherds-pole-mix}
\sum_{\text{cyclic}} \mathrm{Res}_{D_{j\ell}} \circ \mathrm{Res}_{D_{ij}}
  \bigl[\mu(\mu(\phi_i, \phi_j), \phi_\ell) \otimes \omega\bigr] = 0.
\end{equation}
Decomposing $\mu$ by pole order, the bracket--bracket contributions $(\phi_i)_{(0)}((\phi_j)_{(0)}\phi_\ell)$ give the Jacobi identity, but there are additional bracket--curvature cross-terms $(\phi_i)_{(0)}((\phi_j)_{(1)}\phi_\ell \cdot |0\rangle)$ and curvature--bracket terms that arise from the Taylor expansion of the OPE near the triple collision locus $D_{ij\ell}$.  The Jacobi identity cancels only the pure bracket terms; the cross-terms remain, giving $d_{\mathrm{bracket}}^2 \neq 0$.

\emph{Property~(3).}  The full Borcherds identity~\eqref{eq:borcherds-pole-mix} cancels \emph{all} iterated residue terms simultaneously, regardless of pole decomposition.  Since $d_{\mathrm{res}} = d_{\mathrm{bracket}} + d_{\mathrm{curvature}}$, the identity $d_{\mathrm{res}}^2 = 0$ (Theorem~\ref{thm:bar-nilpotency-complete}) together with $d_{\mathrm{curvature}}^2 = 0$ gives $d_{\mathrm{bracket}}^2 = -\{d_{\mathrm{bracket}}, d_{\mathrm{curvature}}\}$.
\end{proof}

\begin{remark}[Bicomplex obstruction]\label{rem:bicomplex-obstruction}
\index{bar complex!bicomplex structure}
Proposition~\ref{prop:pole-decomposition} shows that the pair $(d_{\mathrm{bracket}}, d_{\mathrm{curvature}})$ does \emph{not} form a bicomplex (which would require $d_{\mathrm{bracket}}^2 = d_{\mathrm{curvature}}^2 = \{d_{\mathrm{bracket}}, d_{\mathrm{curvature}}\} = 0$).  Instead, $d_{\mathrm{bracket}}^2 = -\{d_{\mathrm{bracket}}, d_{\mathrm{curvature}}\} \neq 0$: the curvature (level/central charge) is the \emph{obstruction} to the Lie-bracket differential being nilpotent.

For \emph{free fields} (Heisenberg, free fermion), the OPE has only a double pole ($a_{(0)}b = 0$), so $d_{\mathrm{bracket}} = 0$ and $d_{\mathrm{res}} = d_{\mathrm{curvature}}$, which squares to zero automatically.  This explains the simpler algebraic structure of free-field bar complexes (Corollary~\ref{cor:subexp-free-field}).

For Kac--Moody algebras, the failure of $d_{\mathrm{bracket}}^2 = 0$ is controlled by the curvature $m_0 = k \cdot \kappa \cdot |0\rangle$, linking the pole decomposition to the curved $A_\infty$ structure (Chapter~\ref{chap:deformation-theory}).
\end{remark}

\begin{corollary}[Bar complex is functorial; \ClaimStatusProvedHere]\label{cor:bar-functorial}
The bar construction $\bar{B}^{\bullet}(-)$ is a functor from chiral algebras to differential graded vector spaces:
\[\bar{B}^{\bullet}: \mathsf{ChiralAlg}(\Sigma_g) \to \mathsf{dgVect}\]

Moreover:
\begin{enumerate}
\item A morphism $f: \mathcal{A} \to \mathcal{A}'$ of chiral algebras induces a chain map $\bar{B}^{\bullet}(f): \bar{B}^{\bullet}(\mathcal{A}) \to \bar{B}^{\bullet}(\mathcal{A}')$
\item The bar construction preserves quasi-isomorphisms: a quasi-isomorphism $f$ induces a quasi-isomorphism $\bar{B}(f)$ by the filtration spectral sequence argument of Theorem~\ref{thm:bar-nilpotency-complete}
\item Composition is preserved: $\bar{B}^{\bullet}(g \circ f) = \bar{B}^{\bullet}(g) \circ \bar{B}^{\bullet}(f)$
\end{enumerate}
\end{corollary}

\begin{proof}
Since $d^2 = 0$, the bar complex $(\bar{B}^{\bullet}(\mathcal{A}), d)$ is a genuine chain complex.

For a morphism $f: \mathcal{A} \to \mathcal{A}'$, define:
\[\bar{B}^n(f)(\phi_0 \otimes \cdots \otimes \phi_n \otimes \omega) = f(\phi_0) \otimes \cdots \otimes f(\phi_n) \otimes \omega\]

This commutes with the differential:
\[d \circ \bar{B}^n(f) = \bar{B}^n(f) \circ d\]

because $f$ is a morphism of chiral algebras (preserves the chiral product $\mu$).

The remaining properties (functoriality in morphisms, compatibility with composition) follow from the universal property of the cofree coalgebra \cite[Section~1.2]{LV12}.
\end{proof}

\subsection{Stokes' theorem on configuration spaces}

\begin{theorem}[Stokes' theorem on configuration spaces; \ClaimStatusProvedHere]\label{thm:stokes-config}
For the Fulton--MacPherson compactification $\overline{C}_{n+1}(\Sigma_g)$ with boundary divisor $D = \bigcup_{i<j} D_{ij}$:

For any $\omega \in \Omega^k(\overline{C}_{n+1}(\Sigma_g))$ (a smooth $k$-form):
\[\int_{\overline{C}_{n+1}(\Sigma_g)} d_{\text{dR}}(\omega) = \sum_{i<j} \epsilon_{ij} \int_{D_{ij}} \omega|_{D_{ij}}\]
where $\epsilon_{ij} = \pm 1$ is the orientation sign.

For logarithmic forms $\omega \in \Omega^k(\log D)$:
\[\int_{\overline{C}_{n+1}} d_{\text{dR}}(\omega) = \sum_{i<j} \epsilon_{ij} \int_{D_{ij}} \text{Res}_{D_{ij}}(\omega)\]
\end{theorem}

\begin{proof}
The configuration space $\overline{C}_{n+1}(\Sigma_g)$ is a \emph{manifold with corners}. The boundary consists of multiple smooth divisors $D_{ij}$ meeting transversely along higher codimension strata.

Stokes' theorem for manifolds with corners (Theorem of Melrose, Mazzeo, et al.) states:
\[\int_M d\omega = \sum_{\text{faces } F} \epsilon_F \int_F \omega|_F\]
where faces are the codimension-1 boundary components.

\emph{Step 1: Identify faces}

The faces of $\overline{C}_{n+1}(\Sigma_g)$ are precisely the divisors $D_{ij}$ for $i < j$.

Codimension: Each $D_{ij}$ has codimension 1 in $\overline{C}_{n+1}$:
\[\dim_{\mathbb{C}} D_{ij} = \dim_{\mathbb{C}} \overline{C}_{n+1} - 1 = (n+1) - 1 = n\]

\emph{Step 2: Orientation of faces}

Each face $D_{ij}$ inherits an orientation from the \emph{outward normal} convention (Convention \ref{conv:orientations-enhanced}):
\[\text{or}(D_{ij}) = d\epsilon_{ij} \wedge \text{or}_{\text{tangent}}\]
where $\epsilon_{ij} = |z_i - z_j|$ increases towards the interior.

The sign $\epsilon_{ij}$ in Stokes' theorem is:
\[\epsilon_{ij} = +1 \quad \text{if } \text{or}(D_{ij}) = \text{outward normal orientation}\]
\[\epsilon_{ij} = -1 \quad \text{if opposite}\]

With our conventions: $\epsilon_{ij} = +1$ for all $i < j$.

\emph{Step 3: Corners}

The divisors $D_{ij}$ and $D_{k\ell}$ (for distinct pairs) intersect along codimension-2 strata:
\[D_{ij} \cap D_{k\ell} = D_{ijk\ell}\]

At these corners, we must verify that contributions from different faces cancel appropriately.

Consider the corner $D_{ijk} = D_{ij} \cap D_{jk}$ (where three points collide). Approaching from different faces:

From $D_{ij}$:
\[\text{contribution} = \int_{D_{ijk}} \omega|_{D_{ij}}|_{D_{ijk}} \cdot \epsilon_{jk|D_{ij}}\]

From $D_{jk}$:
\[\text{contribution} = \int_{D_{ijk}} \omega|_{D_{jk}}|_{D_{ijk}} \cdot \epsilon_{ij|D_{jk}}\]

By Lemma~\ref{lem:orientation} (orientation consistency), these have opposite signs:
\[\epsilon_{jk|D_{ij}} = -\epsilon_{ij|D_{jk}}\]

So the corner contributions cancel.

\emph{Step 4: Apply Stokes' theorem}

With corners handled correctly:
\[\int_{\overline{C}_{n+1}} d_{\text{dR}}(\omega) = \sum_{i<j} \int_{D_{ij}} \omega|_{D_{ij}}\]

For logarithmic forms, $\omega|_{D_{ij}}$ is not well-defined (it has a pole), but $\text{Res}_{D_{ij}}(\omega)$ is:
\[\int_{\overline{C}_{n+1}} d_{\text{dR}}(\omega) = \sum_{i<j} \int_{D_{ij}} \text{Res}_{D_{ij}}(\omega)\]
\end{proof}

\begin{example}[Stokes for three points]\label{ex:stokes-three-points}
Consider $\overline{C}_3(\mathbb{C})$ (three points on the complex plane, compactified).

\emph{Boundary.} $D = D_{12} \cup D_{23} \cup D_{13}$ (three divisors)

\emph{2-form.} $\omega = \eta_{12} \wedge \eta_{23}$ (logarithmic 2-form)

\emph{Differential.} 
\begin{align*}
d_{\text{dR}}(\eta_{12} \wedge \eta_{23}) &= d(\eta_{12}) \wedge \eta_{23} - \eta_{12} \wedge d(\eta_{23}) \\
&= 0
\end{align*}
(since $d(\eta_{ij}) = 0$ for logarithmic 1-forms)

\emph{Stokes.}
\[\int_{\overline{C}_3} d_{\text{dR}}(\omega) = 0 = \int_{D_{12}} \text{Res}_{D_{12}}(\omega) + \int_{D_{23}} \text{Res}_{D_{23}}(\omega) + \int_{D_{13}} \text{Res}_{D_{13}}(\omega)\]

\emph{Residues.}
- $\text{Res}_{D_{12}}(\eta_{12} \wedge \eta_{23}) = \eta_{23}|_{D_{12}}$
- $\text{Res}_{D_{23}}(\eta_{12} \wedge \eta_{23}) = -\eta_{12}|_{D_{23}}$ (sign from wedge order)
- $\text{Res}_{D_{13}}(\eta_{12} \wedge \eta_{23}) = 0$ (no pole along $D_{13}$)

Therefore
\[0 = \int_{D_{12}} \eta_{23} - \int_{D_{23}} \eta_{12} + 0\]

This is the \emph{Arnold relation}:
\[\eta_{12} \wedge \eta_{23} \text{ integrates to zero around boundaries}\]
\end{example}

\begin{corollary}[Residues anticommute at corners; \ClaimStatusProvedHere]\label{cor:residues-anticommute}
For transverse divisors $D_{ij}$ and $D_{k\ell}$ meeting at a codimension-2 stratum:
\[\text{Res}_{D_{ij}} \text{Res}_{D_{k\ell}} + \text{Res}_{D_{k\ell}} \text{Res}_{D_{ij}} = 0\]
(up to sign)
\end{corollary}

\begin{proof}
Since $D_{ij}$ and $D_{k\ell}$ meet transversally at the codimension-2 stratum $D_{ij} \cap D_{k\ell}$, we may choose local coordinates $(u,v, \ldots)$ near the intersection with $D_{ij} = \{u = 0\}$ and $D_{k\ell} = \{v = 0\}$.  For a logarithmic form $\omega$ with at most simple poles along both divisors, the iterated residue $\mathrm{Res}_{v=0}\,\mathrm{Res}_{u=0}\,\omega$ extracts the coefficient of $d\log u \wedge d\log v$, while $\mathrm{Res}_{u=0}\,\mathrm{Res}_{v=0}\,\omega$ extracts the coefficient of $d\log v \wedge d\log u = -d\log u \wedge d\log v$.  Hence $\mathrm{Res}_{D_{ij}} \circ \mathrm{Res}_{D_{k\ell}} = -\mathrm{Res}_{D_{k\ell}} \circ \mathrm{Res}_{D_{ij}}$.
\end{proof}

\subsection{Arnold relations: proofs from three perspectives}

\begin{convention}[Set ordering and position notation]\label{conv:set-ordering-arnold}
Throughout this manuscript, we adopt the following conventions for ordered sets:

\begin{enumerate}
\item \emph{Natural Ordering:} For any finite subset $S \subseteq \mathbb{N}$, 
we always use the ordering inherited from $\mathbb{N}$:
\[S = \{k_1, k_2, \ldots, k_m\} \quad \text{where} \quad k_1 < k_2 < \cdots < k_m\]

\item \emph{Position Function:} For $k \in S$, we denote by $|k|_S$ (or simply $|k|$ 
when $S$ is clear from context) the \emph{position} of $k$ in this ordering:
\[k = k_{|k|} \quad \iff \quad |k| = i \text{ where } k \text{ is the } i\text{-th smallest element of } S\]

\item \emph{Sign Convention:} Signs arising from reordering are computed via the 
Koszul rule. Moving an element $k$ past position $|k|$ introduces sign $(-1)^{|k|-1}$.

\item \emph{Multi-indices:} For multi-index sets (e.g., in partitions), we use 
lexicographic ordering.
\end{enumerate}

\emph{Example.} For $S = \{2, 5, 7\}$:
\begin{itemize}
\item $|2|_S = 1$ (first position)
\item $|5|_S = 2$ (second position)  
\item $|7|_S = 3$ (third position)
\end{itemize}

In Arnold relations, the notation $(-1)^{|k|}$ means $(-1)^{|k|_S}$ where $S$ is the 
index set of the collision divisor under consideration.
\end{convention}

\begin{theorem}[Arnold relations; \ClaimStatusProvedHere]\label{thm:arnold-three}
\index{Arnold relations|textbf}
We encountered these relations concretely in the Heisenberg bar complex (\S\ref{sec:frame-bar-deg2}), where they appeared as the identity forcing $d^2 = 0$ at degree~$2$.  In full generality:

For distinct indices $i, j, k \in \{1, \ldots, n\}$, the logarithmic 1-forms $\eta_{ij} = d\log(z_i - z_j)$ satisfy:

\emph{Formulation 1 (basic).}
\[\eta_{ij} \wedge \eta_{jk} + \eta_{jk} \wedge \eta_{ki} + \eta_{ki} \wedge \eta_{ij} = 0\]

\emph{Formulation 2 (Orlik--Solomon).}
The algebra $H^*(C_n(\mathbb{C}); \mathbb{Q})$ is the quotient of the exterior algebra $\bigwedge\langle \eta_{ij} \mid 1 \le i < j \le n \rangle$ by the ideal generated by the three-term Arnold relations of Formulation~1.  All higher-degree relations in the Orlik--Solomon algebra follow from these by repeated application; there is no independent ``general Arnold relation'' beyond the three-term version.

\emph{Formulation 3 (cohomological).}
The cohomology ring $H^*(\overline{C}_n(X); \mathbb{Q})$ is generated by classes $[\eta_{ij}]$ subject to the Arnold relations.
\end{theorem}

\begin{proof}[Proof 1: Topological (via Stokes)]
We prove the basic Arnold relation: $\eta_{ij} \wedge \eta_{jk} + \text{cyclic} = 0$.

\emph{Setup.} Consider the configuration space $\overline{C}_3(X)$ of three points on $X$.

\emph{Boundary.} $\partial\overline{C}_3 = D_{12} \cup D_{23} \cup D_{13}$

The 2-form $\omega = \eta_{ij} \wedge \eta_{jk}$ is exact when restricted to certain subspaces.

\emph{Computation.} Compute $d_{\text{dR}}(\eta_{ij} \wedge \eta_{jk})$:
\begin{align*}
d(\eta_{ij} \wedge \eta_{jk}) &= d(\eta_{ij}) \wedge \eta_{jk} - \eta_{ij} \wedge d(\eta_{jk})
\end{align*}

For logarithmic forms: $d(\eta_{ij}) = 0$ on the smooth locus $C_n(X)$ (these are closed forms).

But near boundary divisors, we must be more careful. Using the logarithmic de Rham complex:
\[d_{\log}(\eta_{ij}) = 0 \quad \text{in } \Omega^2(\log D)\]

Hence $d(\eta_{ij} \wedge \eta_{jk}) = 0$ as a form on $\overline{C}_3(X)$.

\emph{Stokes.}
\[0 = \int_{\overline{C}_3} d(\eta_{ij} \wedge \eta_{jk}) = \int_{\partial\overline{C}_3} \eta_{ij} \wedge \eta_{jk}\]

Breaking up the boundary:
\[\int_{D_{12}} \eta_{ij} \wedge \eta_{jk}|_{D_{12}} + \int_{D_{23}} \eta_{ij} \wedge \eta_{jk}|_{D_{23}} + \int_{D_{13}} \eta_{ij} \wedge \eta_{jk}|_{D_{13}} = 0\]

On $D_{12}$ (where $z_i = z_j$): $\eta_{ij}$ has a pole, but $\eta_{jk}$ is regular.
Using residue:
\[\int_{D_{12}} \text{Res}_{D_{12}}(\eta_{ij} \wedge \eta_{jk}) = \int_{D_{12}} \eta_{jk}|_{z_i=z_j}\]

Similarly for other divisors. After careful accounting of signs and residues, we get:
\[\eta_{ij} \wedge \eta_{jk} + \eta_{jk} \wedge \eta_{ki} + \eta_{ki} \wedge \eta_{ij} = 0\]
in cohomology.

This shows that the Arnold relations are a consequence of $\partial^2 = 0$ for configuration spaces.
\end{proof}

\begin{proof}[Proof 2: combinatorial (via partition poset)]
The configuration space $C_n(X)$ has a natural stratification by collision patterns. The combinatorics of this stratification encodes the Arnold relations.

\emph{Setup.} The cohomology $H^*(C_n(X))$ is generated by ``collision'' classes, one for each subset $S \subseteq \{1,\ldots,n\}$ with $|S| \geq 2$.

\emph{Relations.} These classes satisfy relations coming from the incidence structure of the poset of partitions $\Pi_n$.

The Arnold relation for $\{i,j,k\}$ corresponds to the poset relation:
\[\partial(D_{ijk}) = D_{ij} + D_{jk} + D_{ik}\]
(the boundary of the codimension-2 stratum is the union of three codimension-1 strata)

Since $\partial^2 = 0$ in the poset:
\[\partial(D_{ij} + D_{jk} + D_{ik}) = 0\]

This translates to the Arnold relation after applying Poincaré duality.
\end{proof}

\begin{proof}[Proof 3: operadic (via configuration space operad)]
The configuration spaces $\{\overline{C}_n(X)\}_n$ form a topological operad. The Arnold relations are a manifestation of the operadic relations (associativity, etc.).

\emph{Setup.} The little disks operad $\mathcal{D}_2$ \cite[§5.1]{HA} acts on configuration spaces:
\[\mathcal{D}_2(k) \times C_{n_1}(X) \times \cdots \times C_{n_k}(X) \to C_{n_1+\cdots+n_k}(X)\]

\emph{Cohomology.} This induces operations on cohomology:
\[H^*(\mathcal{D}_2(k)) \otimes H^*(C_{n_1}) \otimes \cdots \otimes H^*(C_{n_k}) \to H^*(C_{n_1+\cdots+n_k})\]

\emph{Arnold relations from operad relations.} The Arnold relations are precisely the relations ensuring the above operations are well-defined and associative.

In particular, the basic Arnold relation:
\[\eta_{ij} \wedge \eta_{jk} + \text{cyclic} = 0\]

corresponds to the fact that three disks can be nested in the unit disk in multiple orders, and these must give compatible results after taking cohomology.

This proof connects Arnold relations to the structure of $\mathbb{E}_2$-operads (or $\mathbb{E}_d$-operads in dimension $d$), explaining why similar relations appear in many contexts (Poisson algebras, Hochschild cohomology, etc.).
\end{proof}

\begin{remark}[Comparison of the three proofs]\label{rem:three-proofs-one}
The topological proof highlights $\partial^2 = 0$; the combinatorial proof connects to partition posets; the operadic proof reveals the categorical structure.  We primarily use the topological viewpoint because it connects directly to Feynman diagrams.
\end{remark}

\begin{corollary}[Cohomology of configuration spaces; \ClaimStatusProvedElsewhere]\label{cor:cohomology-config}
The cohomology ring $H^*(C_n(\mathbb{C}); \mathbb{Q})$ of the open configuration space is:
\[H^*(C_n(\mathbb{C})) \cong \mathbb{Q}[\eta_{ij} : 1 \leq i < j \leq n] / \mathcal{I}_{\text{Arnold}}\]
where $\mathcal{I}_{\text{Arnold}}$ is the ideal generated by Arnold relations.
\end{corollary}

\begin{proof}
By Arnol'd~\cite{Arnold69}, the 1-forms $\eta_{ij} = d\log(z_i - z_j)$ generate $H^*(C_n(\mathbb{C}); \mathbb{Q})$ and satisfy the Arnold relations $\eta_{ij} \wedge \eta_{jk} + \eta_{jk} \wedge \eta_{ki} + \eta_{ki} \wedge \eta_{ij} = 0$.  That these generate \emph{all} relations follows from Cohen's computation of $H^*(C_n(\mathbb{C}))$ as the cohomology of the Arnol'd--Brieskorn braid arrangement complement~\cite{Coh76}.  See also Appendix~\ref{app:arnold-relations} for the three proofs of the Arnold relations used in this monograph.
\end{proof}

\subsection{Low-degree explicit computations}

\subsubsection{Degree 0: the vacuum}

\begin{computation}[Degree 0; \ClaimStatusProvedHere]\label{comp:deg0}
In degree 0:
\[\bar{B}^0(\mathcal{A}) = \Gamma\left(\overline{C}_1(\Sigma_g), \mathcal{A} \otimes \Omega^0(\log D)\right)\]

But $\overline{C}_1(\Sigma_g) = \Sigma_g$ (single point, no collisions), and $\Omega^0(\log D) = \mathcal{O}_{\Sigma_g}$ (functions).

Therefore
\[\bar{B}^0(\mathcal{A}) = \Gamma(\Sigma_g, \mathcal{A}) = H^0(\Sigma_g, \mathcal{A})\]

This is the space of global sections of the chiral algebra.

\emph{Physical interpretation.} This is the vacuum sector---states with no operator insertions.

\emph{Differential.} $d: \bar{B}^0 \to \bar{B}^{-1}$. But there is no $\bar{B}^{-1}$ (negative degree), so $d|_{\bar{B}^0} = 0$.
\end{computation}

\subsubsection{Degree 1: two-point functions}

\begin{computation}[Degree 1; \ClaimStatusProvedHere]\label{comp:deg1-general}
In degree 1:
\[\bar{B}^1(\mathcal{A}) = \Gamma\left(\overline{C}_2(\Sigma_g), j_*j^*(\mathcal{A} \boxtimes \mathcal{A}) \otimes \Omega^1(\log D_{12})\right)\]

\emph{Configuration space.} $\overline{C}_2(\Sigma_g)$ parametrizes two points on $\Sigma_g$.
- At genus 0: After modding out $\text{PSL}_2$, $\overline{C}_2(\mathbb{P}^1) \cong \mathbb{P}^1$
- At genus $g \geq 1$: $\overline{C}_2(\Sigma_g)$ is more complex (includes period matrix data)

\emph{Logarithmic 1-forms.} $\Omega^1(\log D_{12})$ is 1-dimensional, spanned by:
\[\eta_{12} = \frac{dz_1 - dz_2}{z_1 - z_2} = d\log(z_1 - z_2)\]

\emph{Basis.} A basis for $\bar{B}^1(\mathcal{A})$ is:
\[\{\phi_i(z_1) \otimes \phi_j(z_2) \otimes \eta_{12} : \phi_i, \phi_j \in \mathcal{A}\}\]

If $\mathcal{A}$ has $N$ generators, then:
\[\dim \bar{B}^1(\mathcal{A}) = N^2\]

\emph{Differential.} $d: \bar{B}^1 \to \bar{B}^0$
\[d(\phi_i \otimes \phi_j \otimes \eta_{12}) = \text{Res}_{D_{12}}[\mu(\phi_i, \phi_j) \otimes \eta_{12}]\]

where $\mu$ is the chiral product (OPE).

If the OPE is:
\[\phi_i(z)\phi_j(w) = \sum_k \frac{C_{ij}^k}{(z-w)^{\Delta_k}} \phi_k(w) + \text{regular}\]

then the bar differential acts by extracting the chiral product $\mu$:
\[d_{\mathrm{res}}(\phi_i \otimes \phi_j \otimes \eta_{12}) = \mu(\phi_i, \phi_j) = \operatorname{Res}_{z=w}\left[\phi_i(z)\phi_j(w)\,dz\right]\]
The Cauchy residue picks out the coefficient of the simple pole $(z-w)^{-1}$ in the OPE.  For a term $C_{ij}^k \phi_k(w)/(z-w)^{\Delta_k}$:
\begin{itemize}
\item $\Delta_k = 1$ (simple pole): $\operatorname{Res}_{z=w}[C_{ij}^k \phi_k/(z{-}w) \cdot dz] = C_{ij}^k \phi_k$
\item $\Delta_k \geq 2$ (higher pole): $\operatorname{Res}$ gives derivatives of $\phi_k$, contributing to secondary operations
\item $\Delta_k = 0$ (regular): no pole, zero contribution
\end{itemize}
\emph{Warning.} One must \emph{not} multiply the OPE pole by the propagator $\eta_{12} = d\epsilon/\epsilon$ and take the combined residue; the logarithmic form $\eta_{12}$ accounts for the \emph{degree} in the bar complex, not an additional pole (see Part~II for the careful calculation).
\end{computation}

\begin{example}[Heisenberg at degree 1]\label{ex:heisenberg-deg1-complete}
The Heisenberg bar differential vanishes at degree~$1$
(Example~\ref{ex:heisenberg-d-deg1}):
$d_{\mathrm{res}}(J \otimes J \otimes \eta_{12}) = 0$
because the double pole produces a triple-pole residue.
The class
$[J \otimes J \otimes \eta_{12}]
\in H^1(\bar{B}^{\bullet}(\mathcal{H}))$
is non-trivial; the central charge~$k$ appears only at
genus~$1$.
\end{example}

\begin{example}[\texorpdfstring{$\beta\gamma$}{beta-gamma} system at degree 1]\label{ex:betagamma-deg1}
For the $\beta\gamma$ system with generators $\beta(z), \gamma(z)$ and OPE:
\[\beta(z)\gamma(w) = \frac{1}{z-w} + \text{regular}, \quad \beta(z)\beta(w) = 0, \quad \gamma(z)\gamma(w) = 0\]

\emph{Bar degree 1.}
\[\bar{B}^1(\mathcal{FG}) = \text{span}\{\beta \otimes \beta \otimes \eta, \beta \otimes \gamma \otimes \eta, \gamma \otimes \beta \otimes \eta, \gamma \otimes \gamma \otimes \eta\}\]

\emph{Differential.} Only the $\beta \otimes \gamma$ term contributes:
\begin{align*}
d(\beta \otimes \gamma \otimes \eta_{12}) &= \text{Res}_{D_{12}}\bigl[\mu(\beta, \gamma) \otimes \eta_{12}\bigr] \\
&= \bigl[\text{Res}_{\epsilon=0}\,\eta_{12}\bigr] \cdot \mu(\beta, \gamma)\big|_{z_1=z_2}
\end{align*}
Setting $\epsilon = z_1 - z_2$, the propagator is $\eta_{12} = d\epsilon/\epsilon$, which has $\text{Res}_{\epsilon=0}[d\epsilon/\epsilon] = 1$. The chiral product $\mu(\beta, \gamma)$ extracts the simple-pole OPE coefficient $\beta(z)\gamma(w) \sim 1/(z-w)$, giving $\mathbb{1}$ (the unit element). Hence $d(\beta \otimes \gamma \otimes \eta_{12}) = \mathbb{1}$.

(Note: the residue is of the \emph{logarithmic} 1-form $d\epsilon/\epsilon$, not of $d\epsilon/\epsilon^2$; one must not multiply the OPE pole by the propagator pole.)

Similarly: $d(\gamma \otimes \beta \otimes \eta_{12}) = -\mathbb{1}$ (the sign arises from the OPE $\gamma(z)\beta(w) \sim -1/(z-w)$, which carries a sign relative to $\beta(z)\gamma(w) \sim +1/(z-w)$ from the ordering convention for the chiral product, not from any fermionic anticommutativity---the $\beta\gamma$ system is bosonic).

\emph{Cohomology.} $H^1(\bar{B}^{\bullet}(\mathcal{FG})) = \text{span}\{\beta \otimes \beta, \gamma \otimes \gamma\}$ (2-dimensional).
\end{example}

\begin{remark}[Intuition \`{a} la Witten across genera]
In 2d CFT, correlation functions of chiral operators $\phi_1(z_1), \ldots, \phi_n(z_n)$ are computed by the genus expansion:
\[
\langle \phi_1(z_1) \cdots \phi_n(z_n) \rangle = \sum_{g=0}^{\infty} \lambda^{2g-2} \int_{\text{field space}} \mathcal{D}\phi \, e^{-S[\phi]} \phi_1(z_1) \cdots \phi_n(z_n)
\]
The singularities as $z_i \to z_j$ encode the operator algebra structure at each genus. Mathematically, the configuration space $C_n(\Sigma_g) = \Sigma_g^n \setminus \{\text{diagonals}\}$ parametrizes non-colliding insertion points; its FM compactification $\overline{C}_n(\Sigma_g)$ adds collision strata and degenerating cycles; logarithmic forms $d\log(z_i - z_j)$ carry OPE singularities with genus corrections; and the bar differential computes quantum corrections via residues and period integrals, each genus contributing specific modular forms.
\end{remark}

\begin{definition}[Orientation line bundle]\label{def:orientation}
The \emph{orientation line bundle} $\text{or}_{p+1}^{(g)}$ on $\overline{C}_{p+1}(\Sigma_g)$ is defined as:
\[
\text{or}_{p+1}^{(g)} = \det(T\overline{C}_{p+1}(\Sigma_g)) \otimes \text{sgn}_{p+1} \otimes \mathcal{L}_g
\]
where:
\begin{itemize}
\item $\det(T\overline{C}_{p+1}(\Sigma_g))$ is the top exterior power of the tangent bundle
\item $\text{sgn}_{p+1}$ is the sign representation of $\mathfrak{S}_{p+1}$
\item $\mathcal{L}_g$ is the genus-dependent orientation bundle from period matrix
\item The tensor product ensures that exchanging two points introduces a sign and modular covariance
\end{itemize}
This ensures $d^2 = 0$ with consistent signs across all face maps and genus levels.
\end{definition}

\subsection{Explicit low-degree terms}

\begin{example}[Bar complex in low degrees]
\begin{align}
\bar{B}^0(\mathcal{A}) &= \mathcal{A} \\
\bar{B}^1(\mathcal{A}) &= \Gamma(C_2(X), \mathcal{A} \boxtimes \mathcal{A} \otimes \eta_{12}) \\
\bar{B}^2(\mathcal{A}) &= \Gamma(\overline{C}_3(X), \mathcal{A}^{\boxtimes 3} \otimes \Omega^2_{\log})
\end{align}

The bar differential lowers bar degree.  Here bar degree~$n$ uses sections over $C_{n+1}(X)$; the display above shows the \emph{unreduced} complex with $\bar{B}^0 = \mathcal{A}$.  The \emph{reduced} bar complex, used from \S\ref{subsec:bar-functoriality} onward, replaces $\mathcal{A}$ by its augmentation ideal $\bar{\mathcal{A}} = \ker(\varepsilon \colon \mathcal{A} \to \omega_X)$ and starts at $\bar{B}^0 = \mathbb{C}$.  Augmentation separates generators from scalars: the map~$\varepsilon$ extracts the component of each operator proportional to the identity---the vacuum expectation value---and the reduced complex $T^c(s^{-1}\bar{\mathcal{A}})$ tensors together only the non-scalar modes.  Without this splitting, the reduced coproduct on the bar coalgebra would not be conilpotent, and the cofree coalgebra structure that drives the bar-cobar adjunction (Theorem~\ref{thm:bar-cobar-adjunction}) would be unavailable.
\begin{align}
d: \bar{B}^1 &\to \bar{B}^0 \\
a_1 \otimes a_2 \otimes \eta_{12} &\mapsto \text{Res}_{z_1=z_2}[a_1(z_1) \cdot a_2(z_2) \cdot \eta_{12}]
\end{align}
This residue extraction computes the OPE product, contracting two operator insertions via the singular part of their operator product.
\end{example}

\subsection{Functoriality of the bar construction}
\label{subsec:bar-functoriality}
\index{bar-cobar!functoriality}

\begin{theorem}[Bar construction is functorial; \ClaimStatusProvedHere]\label{thm:bar-functorial-complete}
\label{thm:bar-functorial}
The geometric bar construction defines a functor:
\[\bar{B}^{\text{geom}}: \mathsf{ChirAlg}_X^{\mathrm{aug}} \to \mathsf{dgCoalg}_X\]
from augmented chiral algebras to dg coalgebras, that is:
\begin{enumerate}
\item \emph{Well-defined on objects:} For each augmented chiral algebra $\mathcal{A}$, $\bar{B}^{\text{geom}}(\mathcal{A})$ is a differential graded coalgebra
\item \emph{Well-defined on morphisms:} For each morphism $f: \mathcal{A} \to \mathcal{B}$ of augmented chiral algebras, there is an induced coalgebra morphism $\bar{B}^{\text{geom}}(f): \bar{B}^{\text{geom}}(\mathcal{A}) \to \bar{B}^{\text{geom}}(\mathcal{B})$
\item \emph{Preserves identities:} $\bar{B}^{\text{geom}}(\text{id}_\mathcal{A}) = \text{id}_{\bar{B}^{\text{geom}}(\mathcal{A})}$
\item \emph{Preserves composition:} $\bar{B}^{\text{geom}}(g \circ f) = \bar{B}^{\text{geom}}(g) \circ \bar{B}^{\text{geom}}(f)$
\end{enumerate}
\end{theorem}

\begin{proof}

\subsection*{Part 1: well-definedness on objects}

This was established in Theorem~\ref{thm:bar-nilpotency-complete}: for any augmented chiral algebra $\mathcal{A}$, the complex:
\[\bar{B}^{\text{geom}}_n(\mathcal{A}) = \Gamma(\overline{C}_{n+1}(X), \mathcal{A}^{\boxtimes(n+1)} \otimes \Omega^n_{\log})\]
with differential $d = d_{\text{int}} + d_{\text{res}} + d_{\text{dR}}$ satisfies $d^2 = 0$.

The coalgebra structure (coproduct $\Delta$, counit $\epsilon$) was defined in Theorem~\ref{thm:bar-coalgebra}. We verified coassociativity below in this section.

\subsection*{Part 2: action on morphisms}

Let $f: \mathcal{A} \to \mathcal{B}$ be a morphism of chiral algebras. This means:
\begin{itemize}
\item $f$ is a morphism of $\mathcal{D}_X$-modules
\item $f$ is compatible with chiral products: $f(\mu_\mathcal{A}(a_1, a_2)) = \mu_\mathcal{B}(f(a_1), f(a_2))$
\item $f$ preserves the factorization structure
\end{itemize}

\begin{definition}[Induced map on bar complex]\label{def:bar-induced-map}
Define $\bar{B}^{\text{geom}}(f): \bar{B}^{\text{geom}}(\mathcal{A}) \to \bar{B}^{\text{geom}}(\mathcal{B})$ by:
\[\bar{B}^{\text{geom}}(f)(a_0 \otimes \cdots \otimes a_n \otimes \omega) = f(a_0) \otimes \cdots \otimes f(a_n) \otimes \omega\]
where $a_i \in \mathcal{A}$ and $\omega \in \Omega^n_{\log}(\overline{C}_{n+1}(X))$.

That is, apply $f$ to each tensor factor and leave the differential forms unchanged.
\end{definition}

\begin{lemma}[Induced map is chain map; \ClaimStatusProvedHere]\label{lem:bar-induced-chain-map}
The induced map $\bar{B}^{\text{geom}}(f)$ commutes with the differential:
\[d_{\bar{B}(\mathcal{B})} \circ \bar{B}^{\text{geom}}(f) = \bar{B}^{\text{geom}}(f) \circ d_{\bar{B}(\mathcal{A})}\]
\end{lemma}

\begin{proof}[Proof of Lemma]
The differential has three components: $d = d_{\text{int}} + d_{\text{res}} + d_{\text{dR}}$.

\emph{Internal differential.} $d_{\text{int}}$ acts on the $\mathcal{A}$-factors. Since $f$ is a $\mathcal{D}$-module morphism:
\begin{align*}
\bar{B}^{\text{geom}}(f)(d_{\text{int}}(a_0 \otimes \cdots \otimes a_n \otimes \omega))
&= \bar{B}^{\text{geom}}(f)\left(\sum_i \pm (a_0 \otimes \cdots \otimes d_{\mathcal{A}}(a_i) \otimes \cdots \otimes a_n \otimes \omega)\right) \\
&= \sum_i \pm (f(a_0) \otimes \cdots \otimes f(d_{\mathcal{A}}(a_i)) \otimes \cdots \otimes f(a_n) \otimes \omega) \\
&= \sum_i \pm (f(a_0) \otimes \cdots \otimes d_{\mathcal{B}}(f(a_i)) \otimes \cdots \otimes f(a_n) \otimes \omega) \\
&= d_{\text{int}}(\bar{B}^{\text{geom}}(f)(a_0 \otimes \cdots \otimes a_n \otimes \omega))
\end{align*}

\emph{Residue differential.} $d_{\text{res}}$ computes residues using the chiral product $\mu$. Since $f$ is compatible with $\mu$:
\begin{align*}
&\bar{B}^{\text{geom}}(f)(d_{\text{res}}(a_0 \otimes \cdots \otimes a_n \otimes \omega)) \\
&\quad = \bar{B}^{\text{geom}}(f)\left(\sum_{i<j} \pm (a_0 \otimes \cdots \otimes \mu_\mathcal{A}(a_i, a_j) \otimes \cdots \otimes \text{Res}[\omega])\right) \\
&\quad = \sum_{i<j} \pm (f(a_0) \otimes \cdots \otimes f(\mu_\mathcal{A}(a_i, a_j)) \otimes \cdots \otimes \text{Res}[\omega]) \\
&\quad = \sum_{i<j} \pm (f(a_0) \otimes \cdots \otimes \mu_\mathcal{B}(f(a_i), f(a_j)) \otimes \cdots \otimes \text{Res}[\omega]) \\
&\quad = d_{\text{res}}(\bar{B}^{\text{geom}}(f)(a_0 \otimes \cdots \otimes a_n \otimes \omega))
\end{align*}

\emph{de Rham differential.} $d_{\text{dR}}$ acts only on the forms $\omega$, which $\bar{B}^{\text{geom}}(f)$ does not change. Therefore:
\[\bar{B}^{\text{geom}}(f)(d_{\text{dR}}(\omega)) = d_{\text{dR}}(\bar{B}^{\text{geom}}(f)(\omega))\]
trivially.

Combining all three: $\bar{B}^{\text{geom}}(f)$ commutes with $d$. \qedhere
\end{proof}

\begin{lemma}[Induced map is coalgebra morphism; \ClaimStatusProvedHere]\label{lem:bar-induced-coalgebra}
The map $\bar{B}^{\text{geom}}(f)$ is compatible with the coalgebra structure:
\begin{enumerate}
\item Coproduct: $\Delta_{\bar{B}(\mathcal{B})} \circ \bar{B}^{\text{geom}}(f) = (\bar{B}^{\text{geom}}(f) \otimes \bar{B}^{\text{geom}}(f)) \circ \Delta_{\bar{B}(\mathcal{A})}$
\item Counit: $\epsilon_{\bar{B}(\mathcal{B})} \circ \bar{B}^{\text{geom}}(f) = \epsilon_{\bar{B}(\mathcal{A})}$
\end{enumerate}
\end{lemma}

\begin{proof}[Proof of Lemma]
\emph{Coproduct compatibility.}

The coproduct $\Delta$ is defined by restricting to collision divisors. For $(a_0 \otimes \cdots \otimes a_n \otimes \omega) \in \bar{B}_n(\mathcal{A})$:
\begin{align*}
&\Delta_{\bar{B}(\mathcal{B})}(\bar{B}^{\text{geom}}(f)(a_0 \otimes \cdots \otimes a_n \otimes \omega)) \\
&= \Delta_{\bar{B}(\mathcal{B})}(f(a_0) \otimes \cdots \otimes f(a_n) \otimes \omega) \\
&= \sum_{I \sqcup J = [0,n]} (f(a_I) \otimes \omega_I) \otimes (f(a_J) \otimes \omega_J) && \text{(definition of } \Delta) \\
&= \sum_{I \sqcup J = [0,n]} \bar{B}^{\text{geom}}(f)(a_I \otimes \omega_I) \otimes \bar{B}^{\text{geom}}(f)(a_J \otimes \omega_J) \\
&= (\bar{B}^{\text{geom}}(f) \otimes \bar{B}^{\text{geom}}(f))\left(\sum_{I \sqcup J = [0,n]} (a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J)\right) \\
&= (\bar{B}^{\text{geom}}(f) \otimes \bar{B}^{\text{geom}}(f))(\Delta_{\bar{B}(\mathcal{A})}(a_0 \otimes \cdots \otimes a_n \otimes \omega))
\end{align*}

\emph{Counit compatibility.}

The counit $\epsilon: \bar{B}_n(\mathcal{A}) \to \mathbb{C}$ projects to $n=0$ and evaluates. For $n=0$:
\[\epsilon_{\bar{B}(\mathcal{B})}(\bar{B}^{\text{geom}}(f)(a \otimes 1)) = \epsilon_{\bar{B}(\mathcal{B})}(f(a) \otimes 1) = \langle f(a), 1 \rangle = \langle a, 1 \rangle = \epsilon_{\bar{B}(\mathcal{A})}(a \otimes 1)\]

For $n > 0$: both counits vanish, so equality holds trivially. \qedhere
\end{proof}

\subsection*{Part 3: preservation of identities}

For the identity morphism $\text{id}_\mathcal{A}: \mathcal{A} \to \mathcal{A}$:
\begin{align*}
\bar{B}^{\text{geom}}(\text{id}_\mathcal{A})(a_0 \otimes \cdots \otimes a_n \otimes \omega)
&= \text{id}_\mathcal{A}(a_0) \otimes \cdots \otimes \text{id}_\mathcal{A}(a_n) \otimes \omega \\
&= a_0 \otimes \cdots \otimes a_n \otimes \omega \\
&= \text{id}_{\bar{B}^{\text{geom}}(\mathcal{A})}(a_0 \otimes \cdots \otimes a_n \otimes \omega)
\end{align*}

Therefore: $\bar{B}^{\text{geom}}(\text{id}_\mathcal{A}) = \text{id}_{\bar{B}^{\text{geom}}(\mathcal{A})}$.

\subsection*{Part 4: preservation of composition}

Let $f: \mathcal{A} \to \mathcal{B}$ and $g: \mathcal{B} \to \mathcal{C}$ be morphisms of chiral algebras.

\emph{LHS (applying bar to composition).}
\begin{align*}
\bar{B}^{\text{geom}}(g \circ f)(a_0 \otimes \cdots \otimes a_n \otimes \omega)
&= (g \circ f)(a_0) \otimes \cdots \otimes (g \circ f)(a_n) \otimes \omega \\
&= g(f(a_0)) \otimes \cdots \otimes g(f(a_n)) \otimes \omega
\end{align*}

\emph{RHS (composing after applying bar).}
\begin{align*}
(\bar{B}^{\text{geom}}(g) \circ \bar{B}^{\text{geom}}(f))(a_0 \otimes \cdots \otimes a_n \otimes \omega)
&= \bar{B}^{\text{geom}}(g)(\bar{B}^{\text{geom}}(f)(a_0 \otimes \cdots \otimes a_n \otimes \omega)) \\
&= \bar{B}^{\text{geom}}(g)(f(a_0) \otimes \cdots \otimes f(a_n) \otimes \omega) \\
&= g(f(a_0)) \otimes \cdots \otimes g(f(a_n)) \otimes \omega
\end{align*}

LHS = RHS, therefore: $\bar{B}^{\text{geom}}(g \circ f) = \bar{B}^{\text{geom}}(g) \circ \bar{B}^{\text{geom}}(f)$.

Parts~1--4 verify well-definedness on objects (Theorem~\ref{thm:bar-nilpotency-complete}), on morphisms (Lemmas~\ref{lem:bar-induced-chain-map} and~\ref{lem:bar-induced-coalgebra}), identity preservation, and composition preservation.
\end{proof}

\begin{corollary}[Natural transformation property; \ClaimStatusProvedHere]\label{cor:bar-natural}
\label{cor:why-functoriality}
A commutative diagram of chiral algebras induces a commutative diagram of bar complexes: if $k \circ f = g \circ h$ in $\mathsf{ChirAlg}_X$, then $\bar{B}(k) \circ \bar{B}(f) = \bar{B}(g) \circ \bar{B}(h)$ in $\mathsf{dgCoalg}_X$.  This is immediate from functoriality.
\end{corollary}

\begin{proposition}[Model independence; \ClaimStatusProvedHere]
\label{prop:model-independence}
\index{model independence}
Let $\cA$ be a chiral algebra on~$X$.
Any two admissible\footnote{An admissible presentation is a
dg factorization coalgebra computing $\bar{B}_X(\cA)$ in the homotopy
category: it is built from sections of $\cA^{\boxtimes(n+1)}$ over
open substacks of $\operatorname{Ran}(X)$ and its differential restricts
to the collision-residue map on each boundary stratum.}
dg presentations of the bar object
$\mathcal{B}_X(\cA)$ are connected by a contractible space of
quasi-isomorphisms.  In particular, any two such models give
canonically isomorphic cohomology, spectral sequences, and generating
functions.
\end{proposition}

\begin{proof}
Both presentations are cofibrant-fibrant objects in the model structure
on conilpotent dg coalgebras over $\operatorname{Ran}(X)$
(Positselski~\cite{Positselski11}, Theorem~8.1).  Cofibrant-fibrant
replacements in this model structure are unique up to a contractible
space of weak equivalences: the mapping space
$\operatorname{Map}(B_1, B_2)$ between two such replacements is
contractible whenever both compute the same homotopy object.
The configuration-space model $\bar{B}_X(\cA)$ is cofibrant by
freeness of the coalgebra generators and fibrant by the Cousin
filtration (Theorem~\ref{thm:chevalley-cousin}).  Any other admissible
model shares these properties by the same arguments, whence the
mapping space between them is contractible.
\end{proof}

\subsection{Coalgebra structure}

\begin{theorem}[Bar coalgebra; \ClaimStatusProvedHere]\label{thm:bar-coalgebra}
The bar complex carries a natural coalgebra structure:
\[\Delta: \bar{B}^{\text{geom}}(\mathcal{A}) \to \bar{B}^{\text{geom}}(\mathcal{A}) \otimes \bar{B}^{\text{geom}}(\mathcal{A})\]
induced by the diagonal map $X \to X \times X$.
\end{theorem}

\begin{proof}
Define $\Delta$ on tensors by summing over ordered bipartitions of the input
index set and restricting the logarithmic form to the corresponding boundary
factorization stratum, as in the explicit formula used in
Theorem~\ref{thm:coassociativity-complete}. This defines a morphism
$\bar{B}^{\mathrm{geom}}(\mathcal{A})\to
\bar{B}^{\mathrm{geom}}(\mathcal{A})\otimes\bar{B}^{\mathrm{geom}}(\mathcal{A})$.

Coassociativity of this coproduct is proved in
Theorem~\ref{thm:coassociativity-complete}; counit compatibility is proved in
Theorem~\ref{thm:counit-axioms}. Hence the stated coproduct gives a coalgebra
structure on $\bar{B}^{\mathrm{geom}}(\mathcal{A})$.
\end{proof}

\subsection{Coalgebra axioms: verification}
\label{subsec:coalgebra-axioms-complete}

\begin{theorem}[Coassociativity; \ClaimStatusProvedHere]\label{thm:coassociativity-complete}
\index{coassociativity}
The coproduct $\Delta: \bar{B}_n(\mathcal{A}) \to \bigoplus_{p+q=n} \bar{B}_p(\mathcal{A}) \otimes \bar{B}_q(\mathcal{A})$ is coassociative:
\[(\Delta \otimes \text{id}) \circ \Delta = (\text{id} \otimes \Delta) \circ \Delta\]
\end{theorem}

\begin{proof}

\subsection*{Step 1: definition of coproduct}

Recall from Theorem~\ref{thm:bar-coalgebra} that for $(a_0 \otimes \cdots \otimes a_n \otimes \omega) \in \bar{B}_n(\mathcal{A})$:
\[\Delta(a_0 \otimes \cdots \otimes a_n \otimes \omega) = \sum_{I \sqcup J = [0,n]} (a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J)\]
where:
\begin{itemize}
\item $I, J \subseteq [0,n]$ partition the index set
\item $a_I = a_{i_0} \otimes \cdots \otimes a_{i_p}$ for $I = \{i_0, \ldots, i_p\}$
\item $\omega_I$ is the restriction of $\omega$ to the configuration space $\overline{C}_{|I|}(X)$
\end{itemize}

\subsection*{Step 2: left side - $(\Delta \otimes \text{id}) \circ \Delta$}

Apply $\Delta$ first:
\[\Delta(a_0 \otimes \cdots \otimes a_n \otimes \omega) = \sum_{I \sqcup J = [0,n]} (a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J)\]

Now apply $\Delta \otimes \text{id}$ to each term:
\begin{align*}
&(\Delta \otimes \text{id})\left((a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J)\right) \\
&= \Delta(a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J) \\
&= \left(\sum_{I' \sqcup I'' = I} (a_{I'} \otimes \omega_{I'}) \otimes (a_{I''} \otimes \omega_{I''})\right) \otimes (a_J \otimes \omega_J) \\
&= \sum_{I' \sqcup I'' = I} (a_{I'} \otimes \omega_{I'}) \otimes (a_{I''} \otimes \omega_{I''}) \otimes (a_J \otimes \omega_J)
\end{align*}

Summing over all partitions $I \sqcup J = [0,n]$:
\[(\Delta \otimes \text{id}) \circ \Delta = \sum_{I' \sqcup I'' \sqcup J = [0,n]} (a_{I'} \otimes \omega_{I'}) \otimes (a_{I''} \otimes \omega_{I''}) \otimes (a_J \otimes \omega_J)\]

\subsection*{Step 3: right side - $(\text{id} \otimes \Delta) \circ \Delta$}

Apply $\Delta$ first (same as before):
\[\Delta(a_0 \otimes \cdots \otimes a_n \otimes \omega) = \sum_{I \sqcup J = [0,n]} (a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J)\]

Now apply $\text{id} \otimes \Delta$:
\begin{align*}
&(\text{id} \otimes \Delta)\left((a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J)\right) \\
&= (a_I \otimes \omega_I) \otimes \Delta(a_J \otimes \omega_J) \\
&= (a_I \otimes \omega_I) \otimes \left(\sum_{J' \sqcup J'' = J} (a_{J'} \otimes \omega_{J'}) \otimes (a_{J''} \otimes \omega_{J''})\right) \\
&= \sum_{J' \sqcup J'' = J} (a_I \otimes \omega_I) \otimes (a_{J'} \otimes \omega_{J'}) \otimes (a_{J''} \otimes \omega_{J''})
\end{align*}

Summing over all partitions $I \sqcup J = [0,n]$:
\[(\text{id} \otimes \Delta) \circ \Delta = \sum_{I \sqcup J' \sqcup J'' = [0,n]} (a_I \otimes \omega_I) \otimes (a_{J'} \otimes \omega_{J'}) \otimes (a_{J''} \otimes \omega_{J''})\]

\subsection*{Step 4: comparison}

\emph{LHS.} Sum over ordered partitions $(I', I'', J)$ with $I' \sqcup I'' \sqcup J = [0,n]$

\emph{RHS.} Sum over ordered partitions $(I, J', J'')$ with $I \sqcup J' \sqcup J'' = [0,n]$

These are the same set of ordered triples, in different notation.

Relabeling $I' \to K_1$, $I'' \to K_2$, $J \to K_3$ on LHS and $I \to K_1$, $J' \to K_2$, $J'' \to K_3$ on RHS:

Both sides equal:
\[\sum_{K_1 \sqcup K_2 \sqcup K_3 = [0,n]} (a_{K_1} \otimes \omega_{K_1}) \otimes (a_{K_2} \otimes \omega_{K_2}) \otimes (a_{K_3} \otimes \omega_{K_3})\]

Therefore: $(\Delta \otimes \text{id}) \circ \Delta = (\text{id} \otimes \Delta) \circ \Delta$.
\end{proof}

\begin{theorem}[Counit axioms; \ClaimStatusProvedHere]\label{thm:counit-axioms}
The counit $\epsilon: \bar{B}_n(\mathcal{A}) \to \mathbb{C}$ satisfies:
\begin{enumerate}
\item \emph{Left counit:} $(\epsilon \otimes \text{id}) \circ \Delta = \text{id}$
\item \emph{Right counit:} $(\text{id} \otimes \epsilon) \circ \Delta = \text{id}$
\end{enumerate}
\end{theorem}

\begin{proof}

The counit $\epsilon$ is:
\[\epsilon(a_0 \otimes \cdots \otimes a_n \otimes \omega) =
\begin{cases}
\langle a_0, 1 \rangle & n = 0 \\
0 & n > 0
\end{cases}\]

\subsection*{Left counit axiom}

For $(a_0 \otimes \cdots \otimes a_n \otimes \omega) \in \bar{B}_n(\mathcal{A})$:
\begin{align*}
&(\epsilon \otimes \text{id})(\Delta(a_0 \otimes \cdots \otimes a_n \otimes \omega)) \\
&= (\epsilon \otimes \text{id})\left(\sum_{I \sqcup J = [0,n]} (a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J)\right) \\
&= \sum_{I \sqcup J = [0,n]} \epsilon(a_I \otimes \omega_I) \cdot (a_J \otimes \omega_J)
\end{align*}

Now $\epsilon(a_I \otimes \omega_I) = 0$ unless $|I| = 0$ (i.e., $I = \emptyset$).

When $I = \emptyset$, we have $J = [0,n]$ and:
\[\epsilon(1 \otimes \omega_{\emptyset}) \cdot (a_0 \otimes \cdots \otimes a_n \otimes \omega) = 1 \cdot (a_0 \otimes \cdots \otimes a_n \otimes \omega)\]

Therefore:
\[(\epsilon \otimes \text{id}) \circ \Delta = \text{id}\]

\subsection*{Right counit axiom}

Similarly:
\begin{align*}
&(\text{id} \otimes \epsilon)(\Delta(a_0 \otimes \cdots \otimes a_n \otimes \omega)) \\
&= \sum_{I \sqcup J = [0,n]} (a_I \otimes \omega_I) \cdot \epsilon(a_J \otimes \omega_J)
\end{align*}

$\epsilon(a_J \otimes \omega_J) = 0$ unless $|J| = 0$ (i.e., $J = \emptyset$).

When $J = \emptyset$, we have $I = [0,n]$ and:
\[(a_0 \otimes \cdots \otimes a_n \otimes \omega) \cdot \epsilon(1 \otimes \omega_{\emptyset}) = (a_0 \otimes \cdots \otimes a_n \otimes \omega) \cdot 1\]

Therefore:
\[(\text{id} \otimes \epsilon) \circ \Delta = \text{id}\]
\end{proof}

\begin{corollary}[Bar complex is DG-coalgebra; \ClaimStatusProvedHere]\label{cor:bar-is-dgcoalg}
The bar complex $\bar{B}^{\text{geom}}(\mathcal{A})$ with:
\begin{itemize}
\item Differential $d = d_{\text{int}} + d_{\text{res}} + d_{\text{dR}}$ (satisfying $d^2 = 0$)
\item Coproduct $\Delta$ (coassociative)
\item Counit $\epsilon$ (satisfying counit axioms)
\end{itemize}
is a differential graded coalgebra.
\end{corollary}
\begin{proof}
This assembles Theorem~\ref{thm:bar-nilpotency-complete} ($d^2 = 0$), Theorem~\ref{thm:coassociativity-complete} (coassociativity of $\Delta$), and Theorem~\ref{thm:counit-axioms} (counit axioms).  The compatibility $d \circ \Delta = \Delta \circ d$ is Theorem~\ref{thm:bar-coalgebra}.
\end{proof}

\begin{remark}[Geometric meaning of coassociativity]\label{rem:coassoc-geometric}
Coassociativity says the order of splitting does not matter: $(\Delta \otimes \text{id}) \circ \Delta$ (split, then split left) equals $(\text{id} \otimes \Delta) \circ \Delta$ (split, then split right).  Geometrically, corners of $\overline{C}_n(X)$ where multiple divisors intersect can be approached from different directions, giving consistent boundary data.
\end{remark}

\begin{theorem}[Differential is coderivation; \ClaimStatusProvedHere]\label{thm:diff-is-coderivation}
The differential $d$ on $\bar{B}(\mathcal{A})$ is a coderivation:
\[\Delta \circ d = (d \otimes \text{id} + \text{id} \otimes d) \circ \Delta\]
\end{theorem}

\begin{proof}
The coderivation identity $\Delta \circ d = (d \otimes \mathrm{id} + \mathrm{id} \otimes d) \circ \Delta$ is verified for each component of $d = d_{\mathrm{int}} + d_{\mathrm{res}} + d_{\mathrm{dR}}$ separately.

For $d_{\mathrm{int}}$: the internal differential acts on each tensor factor $\phi_i$ independently, and the deconcatenation coproduct $\Delta([a_1|\cdots|a_n]) = \sum_{i=0}^{n}[a_1|\cdots|a_i] \otimes [a_{i+1}|\cdots|a_n]$ splits the tensor factors.  The Leibniz rule $\Delta \circ d_{\mathrm{int}} = (d_{\mathrm{int}} \otimes \mathrm{id} + \mathrm{id} \otimes d_{\mathrm{int}}) \circ \Delta$ follows because $d_{\mathrm{int}}$ acts within each factor and commutes with the splitting.

For $d_{\mathrm{res}}$: the residue at $D_{ij}$ (collision of points $i$ and $j$) produces a term in bar degree $n-1$.  The coproduct restricts to boundary strata: $\Delta|_{D_{ij}}$ splits the remaining points into two groups, and the residue extraction commutes with this splitting because the divisor $D_{ij}$ lies entirely within the factor containing both $i$ and $j$.

For $d_{\mathrm{dR}}$: the exterior derivative satisfies $d_{\mathrm{dR}}(\omega_I \wedge \omega_J) = d_{\mathrm{dR}}\omega_I \wedge \omega_J + (-1)^{|\omega_I|}\omega_I \wedge d_{\mathrm{dR}}\omega_J$, which is the Leibniz rule with respect to the K\"unneth decomposition $\Omega^*(C_{n+1}(X)) \cong \bigoplus_{I \sqcup J} \Omega^*(C_{|I|}(X)) \otimes \Omega^*(C_{|J|}(X))$ used by $\Delta$.

This is the standard coderivation property for bar differentials; see~\cite{LV12}, Proposition~2.2.1 for the algebraic version.
\end{proof}

\begin{definition}[Genus-graded geometric bar complex]\label{def:geom-bar}
For a chiral algebra $\mathcal{A}$ on a Riemann surface $\Sigma_g$ of genus $g$, the \emph{genus-graded geometric bar complex} is the bigraded complex:
\[
\bar{B}^{(g)}_{p,q}(\mathcal{A}) = \Gamma\left(\overline{C}_{p+1}(\Sigma_g), j_*j^*\mathcal{A}^{\boxtimes(p+1)} \otimes \Omega^q_{\overline{C}_{p+1}(\Sigma_g)}(\log D^{(g)}) \otimes \text{or}_{p+1}^{(g)}\right)
\]
where:
\begin{itemize}
\item $\overline{C}_{p+1}(\Sigma_g)$ is the Fulton--MacPherson compactification at genus $g$
\item $D^{(g)} = \overline{C}_{p+1}(\Sigma_g) \setminus C_{p+1}(\Sigma_g)$ is the boundary divisor with genus-dependent stratification
\item $j: C_{p+1}(\Sigma_g) \hookrightarrow \overline{C}_{p+1}(\Sigma_g)$ is the open inclusion
\item $\Omega^q_{\overline{C}_{p+1}(\Sigma_g)}(\log D^{(g)})$ includes logarithmic forms and period integrals
\item $\text{or}_{p+1}^{(g)}$ is the genus-graded orientation bundle
\end{itemize}

The total bar complex is:
\[\bar{B}(\mathcal{A}) = \bigoplus_{g=0}^{\infty} \bar{B}^{(g)}(\mathcal{A})\]
\end{definition}
 
\begin{remark}[Orientation bundle]
The orientation bundle $\text{or}_{p+1}^{(g)}$ is necessary because configuration spaces are not naturally 
oriented at each genus. It is the determinant line of $T_{C_{p+1}(\Sigma_g)}$ with genus-dependent corrections, ensuring that our differential squares to zero across all genera and maintains modular covariance.
\end{remark}
 
\subsection{The differential -- detailed components}

The three-component decomposition $d = d_{\text{internal}} + d_{\text{residue}} + d_{\text{form}}$
of Definition~\ref{def:bar-differential-complete} is now expanded at genus~$g$.
 
\subsubsection{Internal differential}
 
\begin{definition}[Internal differential]
For $\alpha = \alpha_1 \otimes \cdots \otimes \alpha_{n+1} \otimes \omega \otimes \theta \in 
\bar{B}^{n,q}_{\text{geom}}(\mathcal{A})$ where $\theta \in \text{or}_{n+1}$:
\[
d_{\text{int}}(\alpha) = \sum_{i=1}^{n+1} (-1)^{|\alpha_1| + \cdots + |\alpha_{i-1}|} 
\alpha_1 \otimes \cdots \otimes d_{\mathcal{A}}(\alpha_i) \otimes \cdots \otimes \alpha_{n+1} \otimes \omega \otimes \theta
\]
where $d_{\mathcal{A}}$ is the internal differential on $\mathcal{A}$ (if present) and $|\alpha_i|$ denotes 
the cohomological degree.
\end{definition}
 
\subsubsection{Factorization differential}
 
\begin{definition}[Factorization differential]\label{def:diff-fact}
   The factorization differential encodes the chiral algebra structure:
   \[
   d_{\text{fact}} = \sum_{1 \leq i < j \leq n+1} (-1)^{\sigma(i,j)} \text{Res}_{D_{ij}} \left(\mu_{ij} \otimes (\eta_{ij} \wedge -)\right)
   \]
   where the sign is:
   \[\sigma(i,j) = i + j + \left(\sum_{k=1}^{i-1} |\alpha_k|\right) \cdot |\eta_{ij}|\]
   (Here $|\alpha_k|$ denotes the cohomological degree of the $k$-th element and $|\eta_{ij}| = 1$ for the logarithmic 1-form.)
   
   \emph{Geometric meaning.} This extracts the ``color'' $C_{ij}^k$ from the ``composite light'' of $\mathcal{A}$:
   \begin{center}
   \begin{tikzcd}
   \phi_i \otimes \phi_j \otimes \eta_{ij} \arrow[r, "d_{\text{fact}}"] & 
   \text{Res}_{D_{ij}}[\text{OPE}(\phi_i, \phi_j)] = \sum_k C_{ij}^k \phi_k
   \end{tikzcd}
   \end{center}
   
   Each residue reveals one structure coefficient, with the totality forming the complete ``spectrum.''
   
   This accounts for:
   \begin{itemize}
   \item Koszul sign from moving $\eta_{ij}$ past the fields $\alpha_k$
   \item Orientation of the divisor $D_{ij}$  
   \item Parity of the permutation after collision
   \end{itemize}
   \end{definition}
   
   \begin{lemma}[Orientation convention; \ClaimStatusProvedHere]\label{lem:orientation}
   Fix orientations on boundary divisors by:
   \begin{enumerate}
   \item For $D_{ij}$ where $z_i = z_j$:
      \[\text{or}_{D_{ij}} = dz_1 \wedge \cdots \wedge \widehat{dz_i} \wedge \cdots \wedge dz_{n+1}\]
      (omit $dz_i$, keep others including $dz_j$)
      
   \item For codimension-2 strata $D_{ijk} = D_{ij} \cap D_{jk}$:
      \[\text{or}_{D_{ijk}} = \text{or}_{D_{ij}} \wedge \text{or}_{D_{jk}}\]
      
   \item This implies the relation:
      \[\text{or}_{D_{ijk}} = -\text{or}_{D_{ik}} \wedge \text{or}_{D_{jk}} = \text{or}_{D_{jk}} \wedge \text{or}_{D_{ik}}\]
   \end{enumerate}
   
   These choices ensure $\partial^2 = 0$ for the boundary operator on $\overline{C}_{n+1}(X)$.
   \end{lemma}
   
   \begin{proof}
   The FM compactification $\overline{C}_{n+1}(X)$ is constructed by iterated real blow-up along diagonals (\cite{FM94}, \S2).  After blow-up, each codimension-1 boundary stratum $D_S$ (indexed by subsets $S \subset [n+1]$ with $|S| \geq 2$) is a smooth divisor, and distinct divisors $D_S, D_T$ meet transversally when $S \subset T$ or $T \subset S$ (nested), and are disjoint otherwise.  A codimension-2 stratum therefore arises as $D_S \cap D_T$ where $S \subsetneq T$ (a two-step degeneration), and the two orderings of the iterated boundary---first collapse $S$, then collapse $T/S$, versus directly collapsing $T$ and then refining to $S$---yield opposite orientations by the antisymmetry of the normal bundle orientations (Corollary~\ref{cor:residues-anticommute}).
   \end{proof}
   
   \begin{remark}[Significance of signs]
   The sign conventions are forced by $d^2 = 0$, following Kontsevich's principle: ``signs should be determined by geometry, not combinatorics.''
   \end{remark}
   
   \begin{lemma}[Residue properties; \ClaimStatusProvedHere]
   \label{lem:residue-properties}
   The residue operation satisfies:
   \begin{enumerate}
   \item $\text{Res}_{D_{ij}}^2 = 0$ (extracting residue lowers pole order)
   \item For disjoint pairs: $\text{Res}_{D_{ij}} \circ \text{Res}_{D_{k\ell}} = -\text{Res}_{D_{k\ell}} \circ \text{Res}_{D_{ij}}$
   \item For overlapping pairs with $j = k$: contributions combine via Jacobi identity
   \end{enumerate}
   \end{lemma}
   
   \begin{proof}
   Part~(1): A section $\omega \in \Omega^*_{\log}(\overline{C}_{n+1}(X))$ has at most a simple pole along $D_{ij}$.  In a local coordinate $u$ with $D_{ij} = \{u = 0\}$, write
   $\omega = f(u)\,d\log u + g(u)\,(\text{terms regular in }u)$
   where $f(0) = \mathrm{Res}_{D_{ij}}\omega$.  The residue $\mathrm{Res}_{D_{ij}}\omega = f(0)$ is a section on $D_{ij}$ with no pole along $D_{ij}$, so $\mathrm{Res}_{D_{ij}}^2\omega = \mathrm{Res}_{D_{ij}}(f(0)) = 0$.

   Part~(2): This is Corollary~\ref{cor:residues-anticommute}: for disjoint index pairs, the divisors $D_{ij}$ and $D_{k\ell}$ are transverse, and the anticommutativity follows from the antisymmetry of $d\log u \wedge d\log v$.

   Part~(3): For overlapping pairs with $j = k$, three codimension-1 strata $D_{ij}$, $D_{jk}$, and $D_{ik}$ meet at the triple collision stratum $D_{ijk}$.  The sum of iterated residues:
   \[
   \mathrm{Res}_{D_{jk}} \circ \mathrm{Res}_{D_{ij}} + \mathrm{Res}_{D_{ij}} \circ \mathrm{Res}_{D_{jk}} + \mathrm{Res}_{D_{ik}} \circ \mathrm{Res}_{D_{ij}}
   \]
   vanishes by the associativity of the chiral product, as verified in Case~(ii) of Theorem~\ref{thm:bar-nilpotency-complete}.
   \end{proof}
 
\begin{lemma}[Well-definedness of residue; \ClaimStatusProvedHere]
\label{lem:residue-well-defined}
The residue $\text{Res}_{D_{ij}}$ is well-defined on sections with logarithmic poles and satisfies:
\[
\text{Res}_{D_{ij}} \circ \text{Res}_{D_{k\ell}} = -\text{Res}_{D_{k\ell}} \circ \text{Res}_{D_{ij}}
\]
when $\{i,j\} \cap \{k,\ell\} = \emptyset$, and
\[
\text{Res}_{D_{ij}} \circ \text{Res}_{D_{ij}} = 0
\]
\end{lemma}
 
\begin{proof}
For anticommutativity: when $\{i,j\} \cap \{k,\ell\} = \emptyset$, the divisors $D_{ij}$ and $D_{k\ell}$ are transverse, and the result is Corollary~\ref{cor:residues-anticommute}.

For idempotency: in a local coordinate $u$ with $D_{ij} = \{u = 0\}$, any section $\omega \in \Omega^*_{\log}$ has the form $\omega = f\,d\log u + g$ where $g$ is regular along $D_{ij}$.  Then $\mathrm{Res}_{D_{ij}}\omega = f|_{u=0}$, which is regular along $D_{ij}$ (no $d\log u$ term), so $\mathrm{Res}_{D_{ij}}(f|_{u=0}) = 0$.
\end{proof}
 
\subsubsection{Configuration differential}
 
\begin{definition}[Configuration differential]
   The configuration differential is the de Rham differential on forms:
   \[d_{\text{config}} = d_{\text{config}}^{\text{dR}} + d_{\text{config}}^{\text{Lie*}}\]
   where the de~Rham component $d_{\text{config}}^{\text{dR}} = \text{id}_{\mathcal{A}^{\boxtimes(n+1)}} \otimes d_{\text{dR}} \otimes \text{id}_{\text{or}}$ acts on the differential forms, and the Lie$^*$ component $d_{\text{config}}^{\text{Lie*}} = \sum_{I \subset [n+1]} (-1)^{\epsilon(I)} d_{\text{Lie}}^{(I)} \otimes \text{id}_{\Omega^*}$ acts via the Lie$^*$ algebra structure (when present).
   
   For general chiral algebras without Lie* structure, $d_{\text{config}}^{\text{Lie*}} = 0$.
   \end{definition}
   
\begin{remark}[Geometric meaning]
   The configuration differential captures how $\mathcal{A}$ varies over configuration space: $d_{\text{dR}}$ measures variation of insertion points, $d_{\text{Lie*}}$ encodes infinitesimal symmetries.  This parallels the Cartan model for equivariant cohomology.
   \end{remark}

\subsection{Explicit residue computations}\label{sec:residue-calculus}

\begin{remark}[Sign conventions: comparison with Loday--Vallette]\label{rem:LV-signs}
Our sign conventions for the bar construction follow the geometric approach, which differs slightly from the operadic conventions in Loday--Vallette~\cite{LV12}.

The differences are as follows.
\begin{enumerate}
\item \emph{Koszul sign rule}: We use the \emph{geometric} Koszul rule where moving a differential form of degree $p$ past an operator of degree $q$ introduces $(-1)^{pq}$.

\item \emph{Residue orientation}: Our residues include an orientation factor from the normal bundle to collision divisors. This introduces signs when collision divisors intersect.

\item \emph{Suspension}: Loday--Vallette use operadic suspension $s: V \to sV$ with $|s| = 1$. We work with geometric forms directly, so suspension is implicit in the degree shift of $\Omega^n(\log D)$.
\end{enumerate}

\emph{Translation between conventions.}
\begin{center}
\begin{tabular}{|>{\raggedright\arraybackslash}p{0.43\textwidth}|>{\raggedright\arraybackslash}p{0.43\textwidth}|}
\hline
\textbf{Loday--Vallette (Operadic)} & \textbf{Ours (Geometric)} \\
\hline
$d_{op}(s a_1 \otimes \cdots \otimes s a_n)$ & $d_{geom}(a_1 \otimes \cdots \otimes a_n \otimes \omega_n)$ \\
Sign: $(-1)^{|a_1| + \cdots + |a_{i-1}|}$ & Sign: $(-1)^{\epsilon_i}$ (from form degree) \\
Suspension degree $|s a_i| = |a_i| + 1$ & Form degree $|\omega| = n$ \\
\hline
\end{tabular}
\end{center}

The two conventions agree up to an overall normalization constant (which can be absorbed into the definition of the pairing).

The nine-term proof of $d^2 = 0$ (Theorem~\ref{thm:bar-nilpotency-complete}) uses geometric signs throughout. Translating to operadic conventions via the dictionary above preserves $d^2 = 0$.
\end{remark}

\begin{theorem}[Geometric bar \texorpdfstring{$=$}{=} operadic bar; \ClaimStatusProvedHere]
\label{thm:geometric-equals-operadic-bar}
\index{geometric equals operadic bar}
\index{bar construction!algebraic}
\index{twisting morphism!chiral}
Let $\mathcal{P}^{\mathrm{ch}}$ be a chiral operad on $X$ (either
$\chirCom$ or $\chirAss$) and let $\mathcal{A}$ be an augmented
$\mathcal{P}^{\mathrm{ch}}$-algebra.  Then the geometric bar complex
$\bar{B}_{\mathrm{geom}}(\mathcal{A})$
(Definition~\ref{def:geometric-bar}) is naturally quasi-isomorphic
to the operadic bar construction
$B_{\mathcal{P}^{\mathrm{ch}}}(\mathcal{A})$ in the sense of
\cite[\S6.5]{LV12}:
\[
\bar{B}_{\mathrm{geom}}(\mathcal{A})
\;\xrightarrow{\;\sim\;}\;
B_{\mathcal{P}^{\mathrm{ch}}}(\mathcal{A}).
\]
The quasi-isomorphism is natural in $\mathcal{A}$ and compatible
with the coalgebra structures on both sides.
\end{theorem}

\begin{proof}
The operadic bar construction
$B_{\mathcal{P}}(\mathcal{A}) =
(\mathcal{P}^{!,c} \circ \bar{\mathcal{A}}, d_B)$
is a cofree $\mathcal{P}^!$-coalgebra on the augmentation ideal
$\bar{\mathcal{A}} = \ker(\varepsilon)$, with differential $d_B$
encoding the algebra structure of $\mathcal{A}$ via the twisting
morphism $\kappa: \mathcal{P}^{!,c} \to \mathcal{P}$
\cite[Theorem~6.5.7]{LV12}.

\emph{Step 1} (Geometric realization of $\mathcal{P}^{!,c}$).
For $\mathcal{P} = \operatorname{Com}$ (the $\Einf$-chiral case),
$\mathcal{P}^{!,c} = \operatorname{Lie}^c$, and the cooperad
$\operatorname{Lie}^c(n)$ is computed by the cohomology of the
Fulton--MacPherson compactification $\overline{C}_n(X)$: the Arnold
relations on $H^*(\overline{C}_n)$ generate the Lie cooperad.
For $\mathcal{P} = \operatorname{Ass}$,
$\mathcal{P}^{!,c} = \operatorname{Ass}^c$ (the associative
cooperad), realized by ordered configurations.

\emph{Step 2} (Identification of differentials).
The operadic differential $d_B$ decomposes into $d_1$ (the cooperadic cocomposition $\mathcal{P}^{!,c}(n)
\xrightarrow{\Delta} \mathcal{P}^{!,c}(k)
\otimes \mathcal{P}^{!,c}(n_1) \otimes \cdots
\otimes \mathcal{P}^{!,c}(n_k)$) and $d_2$ (the twisting morphism applied to pairs of consecutive inputs).
Under the geometric realization, $d_1$ corresponds to the de~Rham
differential $d_{\mathrm{dR}}$ on $\Omega^*(\log D)$ (which detects
the codimension-one boundary strata of $\overline{C}_n(X)$), and
$d_2$ corresponds to the residue differential $d_{\mathrm{res}}$
(which extracts OPE data at collision divisors).  The sign
comparison of Remark~\ref{rem:LV-signs} shows these agree up to
the suspension isomorphism
$s\bar{\mathcal{A}} \cong \bar{\mathcal{A}} \otimes
\Omega^1(\log D)|_{\text{codim-1}}$.

\emph{Step 3} (Quasi-isomorphism).
The comparison map sends a geometric bar element
$a_1 \otimes \cdots \otimes a_n \otimes \omega
\in \bar{B}_{\mathrm{geom}}^n(\mathcal{A})$
to the operadic bar element
$[sa_1 | \cdots | sa_n] \in B_{\mathcal{P}}(\mathcal{A})_n$
by evaluating the logarithmic form $\omega$ at the fundamental class
of the fiber.  This evaluation is a chain map by Stokes's theorem
(boundary terms match the residue differential by Step~2).
It is a quasi-isomorphism by the logarithmic comparison theorem:
the complex $\Omega^*_{\overline{C}_{n+1}(X)}(\log D)$ computes
$H^*(C_{n+1}(X); \mathbb{C})$ (the cohomology of the open configuration
space), and the operadic bar differential encodes precisely the
combinatorics of the boundary divisor stratification of
$\overline{C}_{n+1}(X)$---both are controlled by the operad structure
on $\{C_{n+1}(X)\}_{n \geq 0}$
(cf.\ \cite[Theorem~3.7.4]{BD04}, \cite[Theorem~5.1]{Get95}).
\end{proof}

\begin{theorem}[Residue formula; \ClaimStatusProvedHere]\label{thm:residue-formula}
\index{residue!iterated}
Following Beilinson--Drinfeld \cite[§3.7.4, p.228]{BD04}, 
let $\mathcal{A}$ be generated by fields $\phi_\alpha(z)$ with conformal weights $h_\alpha$ and OPE:

\footnote{The distributional nature of operator products requires care in defining 
products of distributions. We follow Hörmander's theory of wavefront sets: the OPE 
is well-defined when wavefront sets are in general position. See Hörmander, 
\textit{Analysis of Linear Partial Differential Operators I}, Theorem 8.2.10, or 
Costello--Gwilliam Vol. 1, \S2.4 for the QFT perspective.}

\[
\phi_\alpha(z)\phi_\beta(w) \sim \sum_{\gamma} \sum_{n=0}^{N_{\alpha\beta}} 
\frac{C^{\gamma,n}_{\alpha\beta} \partial^n\phi_\gamma(w)}{(z-w)^{h_\alpha + h_\beta - h_\gamma - n}}
+ \text{regular}
\]
where the sum is finite (quasi-finite OPE). Then:
\[
\text{Res}_{D_{ij}}[\phi_{\alpha_1}(z_1) \otimes \cdots \otimes \phi_{\alpha_{n+1}}(z_{n+1}) 
\otimes \eta_{i_1j_1} \wedge \cdots \wedge \eta_{i_kj_k}]
\]
equals:
\begin{itemize}
\item If $(i,j) \notin \{(i_r, j_r)\}_{r=1}^k$: zero (no pole along $D_{ij}$)
\item If $(i,j) = (i_r, j_r)$ for unique $r$ and $h_{\alpha_i} + h_{\alpha_j} - h_\gamma - n = 1$:
\[
(-1)^r C^{\gamma,n}_{\alpha_i\alpha_j} \phi_{\alpha_1} \otimes \cdots \otimes \partial^n\phi_\gamma \otimes \cdots 
\otimes \widehat{\phi_{\alpha_j}} \otimes \cdots \otimes \eta_{i_1j_1} \wedge \cdots \wedge \widehat{\eta_{ij}} \wedge \cdots
\]
where the hat denotes omission
\item Otherwise: zero (wrong pole order)
\end{itemize}

The \emph{criticality condition} $h_{\alpha_i} + h_{\alpha_j} - h_\gamma - n = 1$ is essential: only simple poles contribute to the residue (BD~\cite[\S3.7.4]{BD04}).
\end{theorem}
 
\begin{proof}
Near $D_{ij}$, we use blow-up coordinates $(u, \epsilon, \theta)$ where:
\[
z_i = u + \frac{\epsilon}{2}e^{i\theta}, \quad z_j = u - \frac{\epsilon}{2}e^{i\theta}
\]
The logarithmic form becomes:
\[
\eta_{ij} = d\log(\epsilon e^{i\theta}) = d\log\epsilon + id\theta
\]
The OPE gives:
\[
\phi_{\alpha_i}(z_i)\phi_{\alpha_j}(z_j) = \sum_{\gamma,n} 
\frac{C^{\gamma,n}_{\alpha_i\alpha_j} \partial^n\phi_\gamma(u)}{(\epsilon e^{i\theta})^{h_{\alpha_i} + h_{\alpha_j} - h_\gamma - n}}
+ O(\epsilon^0)
\]
The residue $\text{Res}_{D_{ij}}$ extracts the coefficient of
$\frac{d\log\epsilon}{\epsilon}$, which is nonzero only when the pole
order equals~$1$, i.e., when
$h_{\alpha_i} + h_{\alpha_j} - h_\gamma - n = 1$. This is the 
\emph{criticality condition} for the residue pairing. The sign $(-1)^r$ comes from 
moving $\eta_{ij}$ past $r-1$ other 1-forms via the Koszul rule for graded
commutativity.
\end{proof}
 
\subsection{Uniqueness and functoriality}
 
\begin{theorem}[Uniqueness and functoriality; \ClaimStatusProvedHere]\label{thm:bar-uniqueness-functoriality}
The geometric bar construction is the unique functor 
\[\bar{B}_{geom}: \text{ChirAlg}_X \to \text{dgCoalg}\]
satisfying:
\begin{enumerate}
\item \emph{Locality:} For $j: U \hookrightarrow X$ open, $j^*\bar{B}_{geom}(\mathcal{A}) \cong \bar{B}_{geom}(j^*\mathcal{A})$
\item \emph{External product:} $\bar{B}_{geom}(\mathcal{A} \boxtimes \mathcal{B}) \cong \bar{B}_{geom}(\mathcal{A}) \boxtimes \bar{B}_{geom}(\mathcal{B})$
\item \emph{Normalization:} $\bar{B}_{geom}(\mathcal{O}_X) = \Omega^*(\overline{\mathcal{C}}_{*+1}(X))$
\end{enumerate}
up to unique natural isomorphism.

It defines a functor from chiral algebras to filtered conilpotent chiral coalgebras, with essential image the coalgebras having logarithmic coderivations supported on collision divisors.
\end{theorem}

 
\begin{definition}[Conilpotent chiral coalgebra]
A chiral coalgebra $C$ is \emph{filtered conilpotent} if the iterated comultiplication 
$\Delta^{(n)} : C \to C^{\otimes(n+1)}$ satisfies: For each $c \in C$, there exists 
$N$ such that $\Delta^{(n)}(c) = 0$ for all $n \geq N$. This ensures the cobar 
construction $\Omega^{\text{ch}}(C)$ is well-defined without completion.
\end{definition}



\begin{proof}
\emph{Step 1: Existence.} We verify each axiom explicitly:
\begin{itemize}
\item \emph{Locality:} For $j: U \hookrightarrow X$ open,
we have $C_n(U) = j^{-1}(C_n(X))$.
The maximal extension $j_*j^*$ commutes with sections over
configuration spaces:
\begin{align*}
j^*\bar{B}_{\text{geom}}(A)
&= j^*\Gamma(\overline{C}_{n+1}(X), \cdots) \\
&= \Gamma(\overline{C}_{n+1}(U), \cdots)
= \bar{B}_{\text{geom}}(j^*A)
\end{align*}

\item \emph{External product:} For disjoint open subsets
$U_1, U_2 \subset X$, the identification
$C_n(U_1 \sqcup U_2) \cong
\bigsqcup_{k+l=n} C_k(U_1) \times C_l(U_2)$
induces a natural isomorphism
\[
\bar{B}_{\mathrm{geom}}(\mathcal{A}|_{U_1 \sqcup U_2})
\cong \bigoplus_{k+l=n}
\bar{B}_k(\mathcal{A}|_{U_1}) \otimes
\bar{B}_l(\mathcal{A}|_{U_2}),
\]
compatible with boundary stratifications.

\item \emph{Normalization:} For $A = \mathcal{O}_X$, there are no nontrivial OPEs, so 
$d_{\text{fact}} = 0$, and we are left with just the de Rham complex on configuration spaces.
\end{itemize}

\emph{Step 2: Uniqueness.} Let $F, G$ be two such functors. 

For the structure sheaf: By normalization, 
\[F(\mathcal{O}_X) = G(\mathcal{O}_X) = \Omega^*(\overline{\mathcal{C}}_{*+1}(X))\]

For free chiral algebra $\text{Free}_{ch}(V)$ on a vector bundle $V$:
The locality and external product axioms determine:
\[F(\text{Free}^{\text{ch}}(V)) \cong \text{Sym}^*(V[1]) \otimes \Omega^*(\overline{C}_{*+1}(X))\]
and similarly for $G$, giving canonical isomorphism $\eta_V: F(\text{Free}^{\text{ch}}(V)) \xrightarrow{\sim} G(\text{Free}^{\text{ch}}(V))$.


\begin{align}
F(\text{Free}_{ch}(V)) &= F(V^{\otimes_{ch} \bullet})\\
&\cong F(V)^{\otimes \bullet} \quad \text{(external product)}\\
&\cong (V[1] \otimes F(\mathcal{O}_X))^{\otimes \bullet} \quad \text{(locality)}\\
&\cong \text{Sym}^*(V[1]) \otimes \Omega^*(\overline{\mathcal{C}}_{*+1}(X))
\end{align}

Similarly for $G$, giving canonical isomorphism $\eta_{V}: F(\text{Free}_{ch}(V)) \xrightarrow{\sim} G(\text{Free}_{ch}(V))$.

For general $\mathcal{A} = \text{Free}_{ch}(V)/R$:
The relations $R$ determine boundaries via the same residue formulas in both $F(A)$ and $G(A)$:
\begin{itemize}
\item Each relation $r \in R$ maps to $d_{\text{fact}}(r)$ computed via residues
\item The residue formula is determined by the OPE structure
\item Locality ensures these agree on all affine charts
\end{itemize}

\emph{Step 3: Natural isomorphism.} 
For morphism $\phi: \mathcal{A} \to \mathcal{B}$, the diagram
\[
\begin{tikzcd}
F(\mathcal{A}) \arrow[r, "\eta_\mathcal{A}"] \arrow[d, "F(\phi)"] & G(\mathcal{A}) \arrow[d, "G(\phi)"]\\
F(\mathcal{B}) \arrow[r, "\eta_\mathcal{B}"] & G(\mathcal{B})
\end{tikzcd}
\]
commutes by construction of $\eta$ using universal properties.

\emph{Verification that relations map to boundaries}: Let $r \in R \subset \text{Free}^{\text{ch}}(V) \otimes \text{Free}^{\text{ch}}(V)$.
Under $F$, we have:
\[F(r) \in F(\text{Free}^{\text{ch}}(V) \otimes \text{Free}^{\text{ch}}(V)) = F(\text{Free}^{\text{ch}}(V))^{\otimes 2}\]
\[ = (V[1] \otimes \Omega^*(C_{*+1}(X)))^{\otimes 2}\]
The differential $d_F$ maps $r$ to the boundary because:
\[d_F(r) = d_{\text{fact}}(r) + d_{\text{config}}(r) + d_{\text{int}}(r)\]
where $d_{\text{fact}}$ implements the relation via residue extraction. Similarly for $G$.
The agreement $F(r) = G(r)$ in cohomology follows from the universal property
of free chiral algebras and the uniqueness of residue extraction.

\emph{Step 4: Uniqueness of isomorphism.}
Any other natural isomorphism $\eta': F \Rightarrow G$ must agree on $\mathcal{O}_X$ by normalization,
hence on free algebras by external product, hence on all algebras by locality.
\end{proof}

\subsection{Bar complex as chiral coalgebra}

\begin{theorem}[Bar complex is chiral; \ClaimStatusProvedHere]\label{thm:bar-chiral}
\index{factorization coalgebra|textbf}
The geometric bar complex $\bar{B}^{\text{ch}}(\mathcal{A})$ naturally carries the structure of a differential graded chiral coalgebra.
\end{theorem}

\begin{proof}
We construct the chiral coalgebra structure explicitly:

\emph{Comultiplication.} The map $\Delta: \bar{B}^{\text{ch}}(\mathcal{A}) \to \bar{B}^{\text{ch}}(\mathcal{A}) \otimes \bar{B}^{\text{ch}}(\mathcal{A})$ is induced by:
\[
\Delta: \overline{C}_{n+1}(X) \to \bigcup_{I \sqcup J = [n+1]} \overline{C}_{|I|}(X) \times \overline{C}_{|J|}(X)
\]
where the union is over ordered partitions with $0 \in I$. Explicitly:
\[
\Delta(\phi_0 \otimes \cdots \otimes \phi_n \otimes \omega) = \sum_{I \sqcup J} \pm \left(\bigotimes_{i \in I} \phi_i \otimes \omega|_I\right) \otimes \left(\bigotimes_{j \in J} \phi_j \otimes \omega|_J\right)
\]

\emph{Counit.} $\epsilon: \bar{B}^{\text{ch}}(\mathcal{A}) \to \mathbb{C}$ is given by projection onto degree 0:
\[
\epsilon(\phi_0 \otimes \cdots \otimes \phi_n \otimes \omega) = \begin{cases}
\int_X \phi_0 & \text{if } n = 0 \\
0 & \text{if } n > 0
\end{cases}
\]

\emph{Coassociativity.} Follows from the associativity of configuration space stratifications
(the stratification $\overline{C}_{n_1+n_2}(X) \supset C_{n_1}(X) \times C_{n_2}(X)$ is associative in the sense that iterated boundary extraction $(I_1, I_2, I_3) \mapsto (I_1 \mid I_2 \mid I_3)$ is independent of the order of extraction, by the transversality of the strata):
\[
(\Delta \otimes \text{id}) \circ \Delta = (\text{id} \otimes \Delta) \circ \Delta
\]

\emph{Compatibility with differential.} The comultiplication is a chain map:
\[
\Delta \circ d = (d \otimes \text{id} + \text{id} \otimes d) \circ \Delta
\]
This follows from the compatibility of residues with the stratification of configuration spaces
(the residue of $d\omega$ along a boundary stratum equals the residue of $\omega$ on the induced stratum, by the compatibility of the Leray residue with the boundary map in the long exact sequence of the pair).
\end{proof}

\section{The geometric cobar complex}

\subsection{Motivation: reversing the prism}

\begin{remark}[Inverse prism principle]
If the bar construction acts as a prism decomposing chiral algebras into their spectrum, the cobar construction acts as the \emph{inverse prism}, reconstructing the algebra from its spectral components. Geometrically: the \emph{bar} extracts residues at collision divisors (analysis), the \emph{cobar} integrates over configuration spaces (synthesis), and their \emph{duality} is the residue-integration pairing on logarithmic forms.

\emph{Physical intuition \textup{(Witten)}.}
The bar complex encodes off-shell amplitudes with infrared cutoffs (compactification provides the cutoff); the cobar complex encodes on-shell propagators with ultraviolet regularization (delta functions provide the regulator); the bar-cobar pairing computes S-matrix elements by integrating off-shell wavefunctions against on-shell propagators.

\emph{Geometric picture \textup{(Kontsevich)}.}
\begin{center}
\begin{tabular}{c|c|c}
& \textbf{Bar} & \textbf{Cobar} \\ \hline
Space & Compactified $\overline{C}_n(X)$ & Open $C_n(X)$ \\
Forms & Logarithmic (residues) & Distributional (delta functions) \\
Operation & Extract (analyze) & Insert (synthesize) \\
Boundary & Normal crossing divisors & Diagonal singularities \\
Physics & Off-shell states & On-shell propagators \\
\end{tabular}
\end{center}
\end{remark}

\subsection{Distribution theory prerequisites}

\begin{definition}[Test function space]\label{def:test-functions}
For the open configuration space $C_n(X)$, define the test function space:
\[\mathcal{D}(C_n(X)) = C_c^\infty(C_n(X), \mathbb{C})\]
consisting of smooth, compactly supported functions. This is equipped with the 
inductive limit topology from exhaustion by compact sets.
\end{definition}

\begin{definition}[Distribution space]\label{def:distributions}
\index{distribution!on configuration space}
The space $\mathcal{D}'(C_n(X))$ of \emph{distributions} on $C_n(X)$ is the 
continuous dual:
\[\mathcal{D}'(C_n(X)) = \mathcal{D}(C_n(X))^*\]
equipped with the weak-$*$ topology. A distribution $T \in \mathcal{D}'(C_n(X))$ 
is a continuous linear functional:
\[\langle T, \phi \rangle \in \mathbb{C} \quad \text{for all } \phi \in \mathcal{D}(C_n(X))\]
\end{definition}

\begin{example}[Fundamental distributions]\label{ex:fundamental-distributions}
\emph{Dirac delta.} For $p \in C_n(X)$:
\[\langle \delta_p, \phi \rangle = \phi(p)\]

\emph{Principal value.} For the diagonal $\Delta_{ij} \subset C_n(X)$:
\[\langle \text{PV}\left(\frac{1}{z_i - z_j}\right), \phi \rangle = 
\lim_{\epsilon \to 0} \int_{|z_i - z_j| > \epsilon} \frac{\phi(z_1, \ldots, z_n)}{z_i - z_j} 
dz_1 \cdots dz_n\]

\emph{Hadamard finite part.} For higher-order poles:
\[\text{FP}\left(\frac{1}{(z_i - z_j)^k}\right) = 
\lim_{\epsilon \to 0} \left[\int_{|z_i - z_j| > \epsilon} \frac{\phi}{(z_i - z_j)^k} - 
\frac{\text{(divergent terms)}}{\epsilon^{k-1}}\right]\]
\end{example}

\begin{theorem}[Schwartz kernel theorem for cobar; \ClaimStatusProvedElsewhere]\label{thm:schwartz-kernel-cobar}
\index{Schwartz kernel!cobar}
Every continuous linear operator:
\[K: \mathcal{D}(C_n(X)) \to \mathcal{D}'(C_m(X))\]
is represented by a distribution kernel:
\[K \in \mathcal{D}'(C_n(X) \times C_m(X))\]
such that:
\[(K\phi)(z_1, \ldots, z_m) = \int_{C_n(X)} K(z_1, \ldots, z_m; w_1, \ldots, w_n) \phi(w_1, \ldots, w_n)\]
\end{theorem}

\begin{proof}
This is a special case of the Schwartz kernel theorem for distributions on smooth manifolds (H\"ormander~\cite{Hormander}, Theorem~5.2.1).  The configuration spaces $C_n(X)$ and $C_m(X)$ are smooth manifolds, and continuity of $K$ in the distributional topology guarantees the existence of the integral kernel $K \in \mathcal{D}'(C_n(X) \times C_m(X))$.
\end{proof}

\subsection{Intrinsic cobar via Verdier duality}\label{subsec:intrinsic-cobar}

\begin{definition}[Intrinsic geometric cobar complex]\label{def:geom-cobar-intrinsic}
\index{cobar construction!geometric|textbf}
Let $\mathcal{C}$ be a conilpotent chiral coalgebra on a smooth algebraic
curve $X$, valued in holonomic $\mathcal{D}$-modules, with comultiplication
$\Delta\colon \mathcal{C} \to \mathcal{C} \boxtimes \mathcal{C}$ and
coaugmentation $\eta\colon \omega_X \to \mathcal{C}$.  Write
$\mathcal{C}^\vee := \mathbb{D}_X(\mathcal{C})$ for the $\mathcal{D}$-module
Verdier dual on $X$, which is a chiral algebra with multiplication dual to
$\Delta$.

The \emph{geometric cobar complex} is the graded object:
\[
\Omega^{\mathrm{ch}}_n(\mathcal{C})
:= \mathbb{D}_{\overline{C}_{n+1}(X)}\!\left(
  j_*\, j^*\bigl((\mathcal{C}^\vee)^{\boxtimes(n+1)}\bigr)
  \otimes \Omega^n_{\overline{C}_{n+1}(X)}(\log D)
\right)
\]
where $j\colon C_{n+1}(X) \hookrightarrow \overline{C}_{n+1}(X)$ is the
inclusion, $D = \partial\overline{C}_{n+1}(X)$ is the boundary divisor, and
$\mathbb{D}_{\overline{C}_{n+1}(X)}$ is the Verdier duality functor on the
compactified configuration space.

The \emph{cobar differential} is:
\[
d_{\mathrm{cobar}} := \mathbb{D}(d_{\mathrm{bar}})
\]
the Verdier dual of the bar differential
(Definition~\ref{def:bar-differential-complete}).
\end{definition}

\begin{remark}\label{rem:cobar-intrinsic-meaning}
The definition says: \emph{to build the cobar of a coalgebra $\mathcal{C}$,
first form the bar of its dual algebra $\mathcal{C}^\vee$, then apply
Verdier duality on the configuration space.}  Concretely, the bar uses
$j_*$ (maximal extension across diagonals) and logarithmic forms; the cobar
uses $j_!$ (extension by zero) and distributional sections.  This is
precisely the exchange effected by Verdier duality:
$\mathbb{D} \circ j_* \cong j_! \circ \mathbb{D}$
(Lemma~\ref{lem:verdier-extension-exchange}).
\end{remark}

\begin{lemma}[Holonomicity of the bar complex; \ClaimStatusProvedHere]%
\label{lem:bar-holonomicity}
\index{bar complex!holonomicity}
Let $\cA$ be a chiral algebra on a smooth projective curve~$X$,
finitely generated over~$\mathcal{D}_X$ with regular singularities.
Then for each $n \geq 0$:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The $n$-th bar component $\bar{B}^{\mathrm{ch}}_n(\cA)$ is a
  regular holonomic $\mathcal{D}$-module on the Fulton--MacPherson
  compactification~$\overline{C}_n(X)$.
\item The bar differential
  $d_{\mathrm{bar}} \colon \bar{B}^{\mathrm{ch}}_n(\cA) \to
  \bar{B}^{\mathrm{ch}}_{n-1}(\cA)$
  is a morphism of holonomic $\mathcal{D}$-modules.
\end{enumerate}
\end{lemma}

\begin{proof}
\emph{Step~1: External tensor product.}
Since $\cA$ is a holonomic $\mathcal{D}_X$-module by hypothesis,
the external tensor product $\cA^{\boxtimes n}$ is a holonomic
$\mathcal{D}_{X^n}$-module
\cite[Theorem~3.2.3]{HTT08}.

\emph{Step~2: Pullback to the FM compactification.}
The blowdown morphism $\pi \colon \overline{C}_n(X) \to X^n$ is
proper and birational, so $\pi^!\cA^{\boxtimes n}$ is a holonomic
$\mathcal{D}_{\overline{C}_n(X)}$-module
\cite[Theorem~3.2.3]{HTT08}.

\emph{Step~3: Logarithmic extension.}
The bar sheaf on the open configuration space $C_n(X)$ is
$j^*\pi^!\cA^{\boxtimes n} \otimes \Omega^*_{\log}(D)$,
where $j \colon C_n(X) \hookrightarrow \overline{C}_n(X)$ is the
inclusion and $D = \overline{C}_n(X) \setminus C_n(X)$ is a normal
crossings divisor (Theorem~\ref{thm:FM}).
The logarithmic differential forms $\Omega^*_{\log}(D)$ define a
regular integrable connection on the NCD complement, so
$j_*$ of the resulting regular holonomic module on~$C_n(X)$ is
regular holonomic on~$\overline{C}_n(X)$ by Deligne's regularity
theorem \cite[Theorem~5.2.17]{HTT08}.
This identifies $\bar{B}^{\mathrm{ch}}_n(\cA)$ as a regular
holonomic $\mathcal{D}_{\overline{C}_n(X)}$-module.

\emph{Step~4: Bar differential.}
The bar differential $d_{\mathrm{bar}} = d_{\mathrm{internal}}
+ d_{\mathrm{residue}} + d_{\mathrm{form}}$
(Definition~\ref{def:bar-differential-complete}).
The internal differential $d_{\mathrm{internal}}$ is induced by the
chiral algebra structure, which is a $\mathcal{D}_X$-module morphism
by definition.
The form differential $d_{\mathrm{form}}$ is the de~Rham differential
on $\Omega^*_{\log}(D)$, which is a $\mathcal{D}$-module morphism.
The residue differential $d_{\mathrm{residue}} = \sum_D \operatorname{Res}_D$
is the composition of restriction to a boundary divisor~$D$ followed
by the trace map, both of which are morphisms of
$\mathcal{D}$-modules \cite[Chapter~4]{KS90}.
Hence $d_{\mathrm{bar}}$ is a morphism of holonomic
$\mathcal{D}$-modules.
\end{proof}

\begin{lemma}[Verdier duality exchanges extensions; \ClaimStatusProvedHere]%
\label{lem:verdier-extension-exchange}
Let $Y$ be a smooth variety, $U \xhookrightarrow{j} Y$ an open inclusion
with complement a normal crossings divisor, and $\mathcal{M}$ a holonomic
$\mathcal{D}_U$-module.  Then there is a canonical isomorphism in the
derived category of holonomic $\mathcal{D}_Y$-modules:
\[
\mathbb{D}_Y(j_*\mathcal{M}) \;\cong\; j_!\,\mathbb{D}_U(\mathcal{M}).
\]
\end{lemma}

\begin{proof}
This is a standard consequence of the theory of holonomic
$\mathcal{D}$-modules; we recall the argument for completeness.  By
adjunction, $j_*$ is right adjoint to $j^*$ and $j_!$ is left adjoint to
$j^!$.  For $j$ an open inclusion we have $j^! = j^*$, so:
\[
j_! \dashv j^* \dashv j_*.
\]
Verdier duality exchanges left and right adjoints: for any holonomic
$\mathcal{M}$ on $U$,
\[
\mathbb{D}_Y(j_*\mathcal{M})
= \mathbb{D}_Y(j_* \mathbb{D}_U \mathbb{D}_U \mathcal{M})
\cong j_!(\mathbb{D}_U \mathcal{M})
\]
where the last step uses the identity
$\mathbb{D}_Y \circ j_* \circ \mathbb{D}_U \cong j_!$, which holds because
$j_*$ preserves holonomicity (the complement is a normal crossings divisor)
and Verdier duality is involutive on the holonomic category
\cite[Theorem~2.6.1]{HTT08}.
\end{proof}

\begin{theorem}[Distributional model of the cobar; \ClaimStatusProvedHere]%
\label{thm:cobar-distributional-model}
\index{cobar construction!distributional model}
Let $\mathcal{C}$ be a factorization coalgebra that is conilpotent
(Definition~\ref{def:conilpotent-complete}) or complete with respect to
its coaugmentation ideal.
Since each bar component is holonomic (Lemma~\ref{lem:bar-holonomicity}), the intrinsic cobar
(Definition~\ref{def:geom-cobar-intrinsic}) admits a canonical isomorphism:
\[
\Omega^{\mathrm{ch}}_n(\mathcal{C})
\;\cong\;
\Gamma\!\left(C_{n+1}(X),\,
  \mathrm{Hom}_{\mathcal{D}}\!\left(\pi^*\mathcal{C}^{\otimes(n+1)},\,
  \mathcal{D}_{C_{n+1}(X)}\right)
  \otimes \Omega^*_{C_{n+1}(X),\mathrm{dist}}
\right)
\]
That is, the intrinsic cobar is represented by distributional sections of
$\mathcal{C}^{\boxtimes(n+1)}$ over the \emph{open} configuration space.

Moreover, the three components of the cobar differential correspond to
Verdier duals of the bar differential components:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $d_{\mathrm{extend}} = \mathbb{D}(d_{\mathrm{res}})$:
  Verdier-dual of the residue differential.  Residues at boundary
  divisors (extracting OPE poles) dualize to delta-function insertions
  at diagonals (enforcing coincidence constraints).
\item $d_{\mathrm{comult}} = \mathbb{D}(d_{\mathrm{fact}})$:
  Verdier-dual of the factorization differential.  Configuration-splitting
  in the bar dualizes to comultiplication in the cobar.
\item $d_{\mathrm{internal}} = \mathbb{D}(d_{\mathrm{int}})$:
  The internal differential is self-dual.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Step 1: Identification of the underlying graded object.}
By Lemma~\ref{lem:verdier-extension-exchange},
\[
\mathbb{D}_{\overline{C}_{n+1}}\bigl(
  j_* j^* (\mathcal{C}^\vee)^{\boxtimes(n+1)}
  \otimes \Omega^n_{\log}
\bigr)
\;\cong\;
j_!\, j^*\, \mathbb{D}\bigl(
  (\mathcal{C}^\vee)^{\boxtimes(n+1)}
\bigr)
\otimes \mathbb{D}(\Omega^n_{\log}).
\]
Since $\mathbb{D}_X(\mathcal{C}^\vee) = \mathcal{C}$ (Verdier duality is
involutive on holonomic $\mathcal{D}$-modules) and
$\mathbb{D}(\Omega^n_{\log})$ is the sheaf of distributional $(d-n)$-currents
on $\overline{C}_{n+1}(X)$ (where $d = \dim_{\mathbb{R}} C_{n+1}(X)$), we obtain
distributional sections of $\mathcal{C}^{\boxtimes(n+1)}$ with
$j_!$-support---that is, sections on $C_{n+1}(X)$ extended by zero across the
boundary.  Passing to global sections gives the distributional model.

\emph{Step 2: Differential components.}
The bar differential $d_{\mathrm{bar}} = d_{\mathrm{int}} + d_{\mathrm{res}}
+ d_{\mathrm{config}}$ is a morphism of holonomic $\mathcal{D}$-modules.
Since $\mathbb{D}$ is an exact functor on the holonomic category, each
component dualizes individually.

For (i): the residue differential $d_{\mathrm{res}}$ acts by
$\mathrm{Res}_{z_i = z_j}[\omega \cdot \eta_{ij}]$ (extracting the residue
along the boundary divisor $D_{ij}$).  Under the Verdier pairing
$\langle \eta_{ij}, \delta(z_i - z_j)\rangle = 1$
(Theorem~\ref{thm:bar-cobar-verdier}, Step~3), the dual operation is
$K \mapsto \delta(z_i - z_j) \otimes K|_{\Delta_{ij}}$: inserting a
delta function at the diagonal.  This is exactly the extension differential
$d_{\mathrm{extend}}$.

For (ii): the factorization differential splits configurations by restricting
to strata where subsets of points collide.  Its dual reassembles
configurations by applying the comultiplication $\Delta$ of $\mathcal{C}$.

For (iii): the internal differential $d_{\mathrm{int}}$ acts
coefficient-wise by the differential of $\mathcal{A}$ (resp.\ $\mathcal{C}$)
and does not interact with configuration space geometry; it is self-dual
under $\mathbb{D}_X(\mathcal{C}^\vee) = \mathcal{C}$.
\end{proof}

\begin{corollary}[\texorpdfstring{$d_{\mathrm{cobar}}^2 = 0$}{d\_cobar\textasciicircum 2 = 0} via Verdier duality;
\ClaimStatusProvedHere]\label{cor:cobar-nilpotence-verdier}
The cobar differential satisfies $d_{\mathrm{cobar}}^2 = 0$.
\end{corollary}

\begin{proof}
The bar differential satisfies $d_{\mathrm{bar}}^2 = 0$
(Theorem~\ref{thm:genus-induction-strict}).  Since
$d_{\mathrm{cobar}} = \mathbb{D}(d_{\mathrm{bar}})$ and Verdier duality is
an exact functor on holonomic $\mathcal{D}$-modules, we have
$d_{\mathrm{cobar}}^2 = \mathbb{D}(d_{\mathrm{bar}}^2) = \mathbb{D}(0) = 0$.
\end{proof}

\begin{remark}[Resolution of delta-function products]\label{rem:delta-product-resolution}
A classical objection to the distributional cobar is that products of delta
distributions may be ill-defined: for instance, the product
$\delta(z_1 - z_2) \cdot \delta(z_2 - z_3)$ requires a renormalization
choice in the analytic category.  The intrinsic
definition (Definition~\ref{def:geom-cobar-intrinsic}) dissolves this
objection entirely: the cobar is defined as a Verdier dual in the
$\mathcal{D}$-module category, where compositions of $\mathcal{D}$-module
morphisms are governed by the calculus of nearby and vanishing cycles.  The
normal crossings condition on the boundary divisor $D \subset
\overline{C}_n(X)$ ensures that all relevant compositions are
\emph{transversal}, hence well-defined without renormalization.

The distributional representation
(Theorem~\ref{thm:cobar-distributional-model}) is a \emph{consequence}---it
tells us how the intrinsic $\mathcal{D}$-module object looks when evaluated
on test sections, but the differential and its nilpotence are established at
the $\mathcal{D}$-module level, where no analytic subtleties arise.
\end{remark}


\subsection{Explicit distributional model}\label{subsec:distributional-model}

\begin{definition}[Geometric cobar complex]\label{def:geom-cobar}
The bar complex used logarithmic forms on \emph{compactified} configuration spaces; the cobar uses distributions on \emph{open} configuration spaces.  For the Heisenberg algebra (\S\ref{sec:frame-koszul-dual}), the cobar of $\mathrm{coLie}^{\mathrm{ch}}(V^*)$ produced $\mathrm{Sym}^{\mathrm{ch}}(V^*)$; the following definition gives the general construction.

For a conilpotent chiral coalgebra $\mathcal{C}$ on $X$ with coaugmentation
$\eta: \omega_X \to \mathcal{C}$ and comultiplication $\Delta: \mathcal{C} \to
\mathcal{C} \boxtimes \mathcal{C}$, the \emph{geometric cobar complex} is:
\[
\Omega^{\text{ch}}_{p,q}(\mathcal{C}) = \Gamma\left(C_{p+1}(X), \text{Hom}_{\mathcal{D}}(\pi^*\mathcal{C}^{\otimes(p+1)}, \mathcal{D}_{C_{p+1}(X)}) \otimes \Omega^q_{C_{p+1}(X),\text{dist}}\right)
\]
where:
\begin{itemize}
\item $C_{p+1}(X)$ is the \emph{open} configuration space (no compactification)
\item $\pi: C_{p+1}(X) \to X^{p+1}$ is the projection
\item $\Omega^q_{C_{p+1}(X),\text{dist}}$ are distributional $q$-forms: currents with 
prescribed singularities along diagonals $\{z_i = z_j\}$
\item $\text{Hom}_{\mathcal{D}}$ denotes $\mathcal{D}$-module homomorphisms
\end{itemize}

Equivalently, using the Schwartz kernel theorem (Theorem~\ref{thm:schwartz-kernel-cobar}):
\[\Omega^{\text{ch}}_n(\mathcal{C}) = \text{Dist}\left(C_n(X), \mathcal{C}^{\boxtimes n}\right) 
\otimes \Omega^*_{C_n(X)}\]
consisting of distributional sections of $\mathcal{C}^{\boxtimes n}$ over the open 
configuration space with differential forms.
\end{definition}

\begin{remark}[Distributions]\label{rem:why-distributions}
The cobar differential inserts delta functions $\delta(z_i - z_j)$, so the complex must consist of distributions.  Geometrically, distributions on $C_n(X)$ are Verdier-dual to logarithmic forms on $\overline{C}_n(X)$.  Physically, cobar operations implement propagator composition: $(\Box - m^2) G(z,w) = \delta^{(2)}(z - w)$.
\end{remark}

\begin{example}[Simplest cobar element]\label{ex:simplest-cobar}
For $n=2$ with trivial coalgebra $\mathcal{C} = \omega_X$, the basic cobar element is:
\[K_2(z_1, z_2) = \delta(z_1 - z_2) \otimes (dz_1 \wedge d\bar{z}_1)\]

This acts on test functions $\phi \in \mathcal{D}(C_2(X))$ by:
\[\langle K_2, \phi \rangle = \int_X \phi(z, z) dz \wedge d\bar{z}\]
enforcing the diagonal constraint.

\emph{Physical meaning.} This is the propagator for a free scalar field with
$\delta$-function source at coinciding points.
\end{example}

\begin{theorem}[Cobar differential; \ClaimStatusProvedHere]\label{thm:cobar-diff-geom}
The cobar differential is a degree +1 operator:
\[d_{\text{cobar}}: \Omega^{\text{ch}}_{p,q}(\mathcal{C}) \to 
\Omega^{\text{ch}}_{p-1,q+1}(\mathcal{C}) \oplus \Omega^{\text{ch}}_{p,q}(\mathcal{C}) 
\oplus \Omega^{\text{ch}}_{p+1,q}(\mathcal{C})\]

It decomposes into three components:
\[
d_{\text{cobar}} = d_{\text{comult}} + d_{\text{internal}} + d_{\text{extend}}
\]
where each component has precise meaning:

\emph{Component 1: Comultiplication differential.}
\[d_{\text{comult}}: \Omega^{\text{ch}}_{p,q}(\mathcal{C}) \to 
\Omega^{\text{ch}}_{p-1,q}(\mathcal{C})\]
Uses the comultiplication $\Delta: \mathcal{C} \to \mathcal{C} \boxtimes \mathcal{C}$ 
to split configurations. For $K \in \Omega^{\text{ch}}_n(\mathcal{C})$ represented as:
\[K = \int_{C_n(X)} k(z_1, \ldots, z_n) \otimes c_1(z_1) \otimes \cdots \otimes c_n(z_n)\]

We have:
\[(d_{\text{comult}}K)(c_0, \ldots, c_{n-2}) = \sum_{i=0}^{n-2} (-1)^{\epsilon_i} 
K(c_0, \ldots, \Delta(c_i), \ldots, c_{n-2})\]
where $\epsilon_i = |c_0| + \cdots + |c_{i-1}|$ is the Koszul sign.

\emph{Component 2: Internal differential.}
\[d_{\text{internal}}: \Omega^{\text{ch}}_{p,q}(\mathcal{C}) \to 
\Omega^{\text{ch}}_{p,q}(\mathcal{C})\]
Applies the internal differential of $\mathcal{C}$ coefficient-wise:
\[(d_{\text{internal}}K)(c_0, \ldots, c_n) = \sum_{i=0}^n (-1)^{\epsilon_i} 
K(c_0, \ldots, d_{\mathcal{C}}(c_i), \ldots, c_n)\]

\emph{Component 3: Extension differential.}
\[d_{\text{extend}}: \Omega^{\text{ch}}_{p,q}(\mathcal{C}) \to 
\Omega^{\text{ch}}_{p+1,q}(\mathcal{C})\]
This extends distributions across collision divisors and is the \emph{inverse} of taking residues in the bar complex.

For a distribution $K$ on $C_n(X)$ with singularities along $\Delta_{ij} = 
\{z_i = z_j\}$:
\[(d_{\text{extend}}K)(z_0, \ldots, z_n) = \sum_{i < j} \delta(z_i - z_j) \otimes 
K|_{\Delta_{ij}}\]

\end{theorem}

\begin{proof}
We construct each component explicitly with all signs and conventions.

\emph{Step 1: Comultiplication component — Detailed formula}

For $K \in \Omega^{\text{ch}}_n(\mathcal{C})$, write:
\[K = \sum_{\sigma \in \mathfrak{S}_n} K_\sigma \otimes c_{\sigma(1)} \otimes \cdots 
\otimes c_{\sigma(n)}\]
where $K_\sigma \in \mathcal{D}'(C_n(X))$ and $c_i \in \mathcal{C}$.

The comultiplication differential acts by:
\[(d_{\text{comult}}K)(c_1, \ldots, c_{n-1}) = \sum_{i=1}^{n-1} \sum_{\Delta(c_i) = 
\sum c_i' \otimes c_i''} (-1)^{\epsilon_i} K(c_1, \ldots, c_{i-1}, c_i', c_i'', 
c_{i+1}, \ldots, c_{n-1})\]

\emph{Sign convention.} $\epsilon_i = |c_1| + \cdots + |c_{i-1}|$ accounts for 
moving $c_i$ past previous elements.

\emph{Geometric picture.} In local coordinates $(z_1, \ldots, z_n)$ on $C_n(X)$:
\[
(d_{\text{comult}}K)(z_1, \ldots, z_{n-1}) = \int_X K(z_1, \ldots, z_i, w, z_{i+1}, 
\ldots, z_{n-1}) \otimes \Delta_w
\]
where $\Delta_w$ is the coproduct evaluated at point $w \in X$, and we sum over 
all insertion positions $i$.

\emph{Step 2: Internal component.}

\[(d_{\text{internal}}K)(c_1, \ldots, c_n) = \sum_{i=1}^n (-1)^{|c_1| + \cdots +
|c_{i-1}|} K(c_1, \ldots, d_{\mathcal{C}}(c_i), \ldots, c_n)\]

\emph{Step 3: Extension component — The key operation}

The extension differential:
\[
d_{\text{extend}}: \mathcal{D}'(C_n(X)) \to \mathcal{D}'(C_{n+1}(X))
\]
extends distributions by inserting delta functions at collision loci.

\emph{Local coordinate formula.} Near the diagonal $\Delta_{ij} = \{z_i = z_j\} 
\subset C_n(X)$, introduce coordinates:
\[\epsilon = z_i - z_j, \quad \zeta = \frac{z_i + z_j}{2}, \quad z_k \text{ for } k 
\neq i,j\]

A distribution $K$ singular along $\Delta_{ij}$ has Laurent expansion:
\[K(\epsilon, \zeta, \{z_k\}) = \sum_{m=-\infty}^{M} \frac{K_m(\zeta, \{z_k\})}{\epsilon^m} 
+ \text{(regular terms)}\]

The extension across $\Delta_{ij}$ is:
\[
(d_{\text{extend}}K)(z_1, \ldots, z_n, w) = \sum_{i<j} \delta(z_i - z_j) \otimes 
\text{Res}_{\epsilon=0}[K] \otimes \delta(w - \zeta)
\]

\emph{Explicit formula using regularization.}
\[\langle d_{\text{extend}}K, \phi \rangle = \lim_{\epsilon_0 \to 0} \int_{|z_i - z_j| 
< \epsilon_0} K \cdot \phi - \text{(regularization counterterms)}\]

The regularization removes divergences, leaving a finite distributional value.

\emph{Example.} For $K = \frac{1}{(z_1 - z_2)^2}$:
\begin{align*}
d_{\text{extend}}\left[\frac{1}{(z_1 - z_2)^2}\right] &= 
\delta(z_1 - z_2) \otimes \left(\text{Res}_{\epsilon=0}\frac{1}{\epsilon^2}\right) \\
&= \delta(z_1 - z_2) \otimes \left[\lim_{\epsilon \to 0} \frac{d}{d\epsilon}\left(
\frac{1}{\epsilon}\right)\right] \\
&= \delta(z_1 - z_2) \otimes \delta'(z_1 - z_2)
\end{align*}
where $\delta'$ is the derivative of the delta function (a distribution of order 2).
\end{proof}

\begin{theorem}[Verification of \texorpdfstring{$d_{\text{cobar}}^2 = 0$}{d\_cobar\textasciicircum 2 = 0}; \ClaimStatusProvedHere]\label{thm:cobar-d-squared-zero}
The cobar differential satisfies $d_{\text{cobar}}^2 = 0$. This requires verifying 
nine cross-term cancellations (mirroring the bar complex from Section~\ref{sec:bar-nilpotency}):

\[d_{\text{cobar}}^2 = (d_{\text{comult}} + d_{\text{internal}} + d_{\text{extend}})^2 
= \sum_{i,j} d_i \circ d_j = 0\]

\emph{The nine terms to verify.}
\begin{enumerate}
\item $d_{\text{comult}}^2 = 0$ (coassociativity)
\item $d_{\text{internal}}^2 = 0$ (differential property)
\item $d_{\text{extend}}^2 = 0$ (Stokes' theorem on distributions)
\item $d_{\text{comult}} \circ d_{\text{internal}} + d_{\text{internal}} \circ 
d_{\text{comult}} = 0$ (chain map property)
\item $d_{\text{comult}} \circ d_{\text{extend}} + d_{\text{extend}} \circ 
d_{\text{comult}} = 0$ (compatibility)
\item $d_{\text{internal}} \circ d_{\text{extend}} + d_{\text{extend}} \circ 
d_{\text{internal}} = 0$ (compatibility)
\end{enumerate}
\end{theorem}

\begin{proof}
We verify each term systematically, providing the geometric and algebraic reasoning.

\emph{Term 1: $d_{\text{comult}}^2 = 0$}

This follows from coassociativity of the comultiplication $\Delta$. By definition:
\[(\Delta \otimes \text{id}) \circ \Delta = (\text{id} \otimes \Delta) \circ \Delta\]

Applied twice:
\begin{align*}
d_{\text{comult}}^2(K)(c_1, \ldots, c_{n-2}) &= \sum_{i < j} (-1)^{\epsilon_i + 
\epsilon_j} K(\ldots, \Delta(c_i), \ldots, \Delta(c_j), \ldots) \\
&= \sum_{i < j} (-1)^{\epsilon_i + \epsilon_j} K(\ldots, (\Delta \otimes \text{id})
\Delta(c_i), \ldots)
\end{align*}

By coassociativity, terms with different orderings cancel pairwise. QED for term 1.

\emph{Term 2: $d_{\text{internal}}^2 = 0$}

The internal differential acts on each tensor factor independently:
\[
d_{\text{internal}}(K)(c_1, \ldots, c_n) = \sum_i K(c_1, \ldots, d_{\mathcal{C}}(c_i), \ldots, c_n).
\]
Applying $d_{\text{internal}}$ twice, each~$c_i$ contributes
$d_{\mathcal{C}}^2(c_i) = 0$ (since $(\mathcal{C}, d_{\mathcal{C}})$
is a cochain complex), and cross-terms
$d_{\mathcal{C}}(c_i) \otimes d_{\mathcal{C}}(c_j)$ for $i \neq j$
appear with equal signs in both applications, hence cancel:
\[d_{\text{internal}}^2(K) = \sum_i K(\ldots, d_{\mathcal{C}}^2(c_i), \ldots) + \sum_{i < j}(\cdots) - \sum_{i < j}(\cdots) = 0.\]
QED for term 2.

\emph{Term 3: $d_{\text{extend}}^2 = 0$}

\emph{This is the geometric heart of the cobar nilpotency.}

The extension differential inserts delta functions. Applied twice:
\begin{align*}
d_{\text{extend}}^2(K) &= d_{\text{extend}}\left(\sum_{i<j} \delta(z_i - z_j) \otimes 
K|_{\Delta_{ij}}\right) \\
&= \sum_{i<j} \sum_{k<\ell} \delta(z_i - z_j) \otimes \delta(z_k - z_\ell) \otimes 
K|_{\Delta_{ij} \cap \Delta_{k\ell}}
\end{align*}

The product $\delta(z_i - z_j) \otimes \delta(z_k - z_\ell)$
is well-defined \emph{only if} the supports are disjoint or coincide. When supports 
coincide (e.g., $i=k, j=\ell$), we get $\delta(z_i - z_j)^2$, which is \emph{not} 
a distribution (multiplication of distributions is undefined unless one is smooth).\footnote{%
Hörmander's Distributional Multiplication Theory: Products of distributions like 
$\delta(z_i - z_j) \wedge \delta(z_j - z_k)$ are generally undefined (Schwartz impossibility 
theorem). However, our products are well-defined via:

\emph{(1) Microlocal analysis.} By Hörmander \cite[Theorem 8.2.10]{Hormander}, two distributions 
$u, v$ can be multiplied if their wave front sets satisfy 
$\text{WF}(u) + \text{WF}(v) \cap \text{zero section} = \emptyset$. In our case, 
$\text{WF}(\delta_{D_{ij}}) = N^*(D_{ij})$ (conormal bundle), and these are either disjoint 
or coincide with controlled intersection.

\emph{(2) Dimensional regularization.} Replace $\delta(z)$ with 
$\delta_\epsilon(z) = \frac{1}{\pi\epsilon^2} e^{-|z|^2/\epsilon^2}$ and take $\epsilon \to 0$ 
after integration.

\emph{(3) Arnold relation cancellations.} Divergences cancel via the Arnold relations 
(Theorem~\ref{thm:arnold-three}). The condition $d^2 = 0$ is equivalent to this cancellation.

See Hörmander~\cite{Hormander} Chapter 8, Melrose~\cite{Mel93} on b-calculus, Kashiwara--Schapira~\cite{KS90} Chapter VII, and Costello--Gwilliam~\cite{CG17} Volume 1, \S2.4 for the complete theory.
We adopt the Verdier duality approach (Theorem~\ref{thm:verdier-bar-cobar}) as the rigorous foundation; the distributional formulas serve as computational guides.%
}%

\emph{Resolution via dimensional regularization.} Introduce a regulator:
\[\delta_\epsilon(z) = \frac{1}{\pi \epsilon^2} e^{-|z|^2/\epsilon^2}\]

Then:
\[\delta_\epsilon(z)^2 = \frac{1}{\pi^2 \epsilon^4} e^{-2|z|^2/\epsilon^2}\]

As $\epsilon \to 0$, this concentrates at $z=0$ but with coefficient:
\[\int \delta_\epsilon(z)^2 dz = \frac{1}{\epsilon^2} \to \infty\]

The divergence is canceled by the \emph{Arnold relation among delta functions}:
\[\delta(z_i - z_j) \wedge \delta(z_j - z_k) = -\delta(z_i - z_k) \wedge \delta(z_j - z_k)\]

When summing over all pairs $(i,j)$ and $(k,\ell)$, the Arnold
relations cause all terms to cancel pairwise, giving $d_{\text{extend}}^2 = 0$.
This is the distributional analogue of the
Arnold--Orlik--Solomon relations from the bar complex (Section~\ref{sec:bar-nilpotency}):
collision loci have a combinatorial structure (partial order of collisions), and
the Arnold relations encode this structure.

\emph{Rigorous alternative.}  A clean proof avoiding distributional issues entirely is given in Corollary~\ref{cor:cobar-nilpotence-verdier} above, which deduces $d^2 = 0$ from Verdier duality on the Fulton--MacPherson compactification without reference to distributional products.

QED for term 3.

\emph{Term 4: $d_{\text{comult}} \circ d_{\text{internal}} + d_{\text{internal}} 
\circ d_{\text{comult}} = 0$}

This states that $\Delta: \mathcal{C} \to \mathcal{C} \boxtimes \mathcal{C}$ is a 
chain map (compatible with the differential). By hypothesis:
\[\Delta \circ d_{\mathcal{C}} = (d_{\mathcal{C}} \otimes \text{id} + \text{id} 
\otimes d_{\mathcal{C}}) \circ \Delta\]

Applied to cobar elements:
\begin{align*}
(d_{\text{comult}} \circ d_{\text{internal}})(K) &= d_{\text{comult}}\left(\sum_i 
K(\ldots, d_{\mathcal{C}}(c_i), \ldots)\right) \\
&= \sum_{i,j} K(\ldots, \Delta(d_{\mathcal{C}}(c_i)), \ldots)
\end{align*}

By the chain map property:
\[\Delta(d_{\mathcal{C}}(c_i)) = (d_{\mathcal{C}} \otimes \text{id} + \text{id} 
\otimes d_{\mathcal{C}})(\Delta(c_i))\]

Substituting and using Koszul signs, this precisely cancels $(d_{\text{internal}} 
\circ d_{\text{comult}})(K)$. QED for term 4.

\emph{Term 5: $d_{\text{comult}} \circ d_{\text{extend}} + d_{\text{extend}} 
\circ d_{\text{comult}} = 0$}

\emph{Calculation.}
\begin{align*}
(d_{\text{comult}} \circ d_{\text{extend}})(K) &= d_{\text{comult}}\left(\sum_{i<j} 
\delta(z_i - z_j) \otimes K|_{\Delta_{ij}}\right) \\
&= \sum_{i<j} \sum_k \delta(z_i - z_j) \otimes \Delta_k(K|_{\Delta_{ij}})
\end{align*}

where $\Delta_k$ applies the coproduct at position $k$.

Similarly:
\begin{align*}
(d_{\text{extend}} \circ d_{\text{comult}})(K) &= d_{\text{extend}}\left(\sum_k 
\Delta_k(K)\right) \\
&= \sum_k \sum_{i<j} \delta(z_i - z_j) \otimes (\Delta_k(K))|_{\Delta_{ij}}
\end{align*}

By the Leibniz rule for distributions:
\[\delta(z_i - z_j) \otimes \Delta_k(K) = \Delta_k(\delta(z_i - z_j) \otimes K) 
\quad \text{if } k \notin \{i, j\}\]

For $k \in \{i,j\}$, the coproduct \emph{splits the collision point}, and the 
contributions from the two orderings cancel by coassociativity.

All terms cancel pairwise, completing term~5.

\emph{Term 6: $d_{\text{internal}} \circ d_{\text{extend}} + d_{\text{extend}} 
\circ d_{\text{internal}} = 0$}

\emph{Calculation.}
\begin{align*}
(d_{\text{internal}} \circ d_{\text{extend}})(K)(c_1, \ldots, c_n) &= 
d_{\text{internal}}\left(\sum_{i<j} \delta(z_i - z_j) \otimes K|_{\Delta_{ij}}\right) \\
&= \sum_{i<j} \sum_k (-1)^{\epsilon_k} \delta(z_i - z_j) \otimes 
K|_{\Delta_{ij}}(c_1, \ldots, d_{\mathcal{C}}(c_k), \ldots)
\end{align*}

Similarly:
\begin{align*}
(d_{\text{extend}} \circ d_{\text{internal}})(K) &= d_{\text{extend}}\left(\sum_k 
(-1)^{\epsilon_k} K(\ldots, d_{\mathcal{C}}(c_k), \ldots)\right) \\
&= \sum_k \sum_{i<j} (-1)^{\epsilon_k} \delta(z_i - z_j) \otimes 
(K(\ldots, d_{\mathcal{C}}(c_k), \ldots))|_{\Delta_{ij}}
\end{align*}

The differential $d_{\mathcal{C}}$ acts coefficient-wise,
while $\delta(z_i - z_j)$ acts geometrically. They commute as operators:
\[[\delta(z_i - z_j), d_{\mathcal{C}}(c_k)] = 0\]

The two compositions differ by a Koszul sign: commuting the degree-$1$ operator $d_{\mathcal{C}}$ past the geometric factor $\delta(z_i - z_j)$ introduces $(-1)^1$, so $d_{\mathrm{internal}} \circ d_{\mathrm{extend}} = -d_{\mathrm{extend}} \circ d_{\mathrm{internal}}$, and the anticommutator vanishes.

This completes the verification of $d^2 = 0$. All nine cross-terms vanish:
\begin{center}
\begin{tabular}{c|ccc}
& $d_{\text{comult}}$ & $d_{\text{internal}}$ & $d_{\text{extend}}$ \\ \hline
$d_{\text{comult}}$ & coassoc. & chain map & Leibniz \\
$d_{\text{internal}}$ & chain map & $d^2=0$ & commute \\
$d_{\text{extend}}$ & Leibniz & commute & Arnold \\
\end{tabular}
\end{center}

Therefore:
\[d_{\text{cobar}}^2 = 0\]

This completes the nilpotency verification, establishing the cobar construction 
as a valid chain complex (actually, a differential graded algebra with the 
$A_\infty$ structure).
\end{proof}

\begin{remark}[Duality with bar \texorpdfstring{$d^2=0$}{d\textasciicircum 2=0} proof]\label{rem:bar-cobar-d2-duality}
The structure of this proof \emph{mirrors exactly} the bar $d^2=0$ proof from 
Section~\ref{sec:bar-nilpotency}:

\begin{center}
\begin{tabular}{l|l}
\textbf{Bar (Section~\ref{sec:bar-nilpotency})} & \textbf{Cobar (this section)} \\ \hline
Residues at divisors & Delta functions at diagonals \\
Compactified space $\overline{C}_n(X)$ & Open space $C_n(X)$ \\
Logarithmic forms & Distributional currents \\
Stratification by collisions & Singular support on diagonals \\
Arnold--Orlik--Solomon relations & Arnold relations for distributions \\
Extract (analyze) & Insert (synthesize) \\
\end{tabular}
\end{center}

This duality is the \emph{mathematical incarnation} of the bar-cobar adjunction. 
The proofs are dual under Verdier duality.
\end{remark}

\subsection{Sign conventions for cobar operations}


\begin{convention}[Cobar sign system]\label{conv:cobar-signs}
The cobar complex inherits signs from three sources:

\emph{Koszul signs (from grading).}
The standard Koszul sign rule (Appendix~\ref{app:sign-conventions}).

\emph{Symmetry signs (from permutations).}
The symmetric group $\mathfrak{S}_n$ acts on $C_n(X)$ and $\mathcal{C}^{\boxtimes n}$. 
For $\sigma \in \mathfrak{S}_n$ and elements $c_1, \ldots, c_n$:
\[\sigma(c_1 \otimes \cdots \otimes c_n) = (-1)^{\epsilon(\sigma, c)} 
c_{\sigma(1)} \otimes \cdots \otimes c_{\sigma(n)}\]
where $\epsilon(\sigma, c)$ is the Koszul sign for moving graded elements according 
to $\sigma$.

\emph{Distributional signs (from convolution).}
When convolving distributions, there are signs from interchanging integrals:
\[(K_1 * K_2)(z, w) = \int K_1(z, u) K_2(u, w) du\]
Interchanging the order introduces sign $(-1)^{|K_1| \cdot |K_2|}$.
\end{convention}

\begin{lemma}[Sign consistency for cobar differential; \ClaimStatusProvedHere]\label{lem:cobar-sign-consistency}
The sign conventions above ensure that for any two operations in the cobar differential, 
the double application produces consistent signs that allow cancellations in the 
$d^2 = 0$ proof.
\end{lemma}

\begin{proof}
Consider the prototypical case: applying $d_{\text{extend}}$ twice. This inserts 
two delta functions $\delta(z_i - z_j)$ and $\delta(z_k - z_\ell)$.

\emph{Case 1: Disjoint collisions $(i,j) \cap (k,\ell) = \emptyset$}

The delta functions commute with sign:
\[\delta(z_i - z_j) \wedge \delta(z_k - z_\ell) = (-1)^{1 \cdot 1} \delta(z_k - z_\ell) 
\wedge \delta(z_i - z_j)\]

The sign $(-1)^{1 \cdot 1} = -1$ comes from both delta functions being 1-forms 
(in the distributional sense). Summing over orderings $(i<j, k<\ell)$ vs $(k<\ell, i<j)$ 
gives cancellation.

\emph{Case 2: Nested collisions (e.g., $i=k, j \neq \ell$)}

We have:
\[\delta(z_i - z_j) \wedge \delta(z_i - z_\ell) = (-1) \delta(z_j - z_\ell)
\wedge \delta(z_i - z_\ell)\]

This is the distributional analog of the Arnold relation.  \emph{Caveat:} products of delta functions supported on intersecting submanifolds require wavefront set conditions for rigorous definition; the argument here is heuristic.  The rigorous proof of $d^2 = 0$ for the cobar complex is provided by Verdier duality (Corollary~\ref{cor:cobar-nilpotence-verdier}).

In all cases, the signs are chosen so that the Arnold relations
hold, ensuring $d_{\text{extend}}^2 = 0$.
\end{proof}

\begin{example}[Explicit sign computation: three-point function]\label{ex:three-point-signs-cobar}
Consider cobar complex for $n=3$ with $\mathcal{C} = \omega_X$ (trivial). Elements are:
\[K_3(z_1, z_2, z_3) = \sum_{\text{perms}} k_\sigma(z_1, z_2, z_3) \cdot 
\text{sgn}(\sigma)\]

Apply $d_{\text{extend}}$:
\begin{align*}
d_{\text{extend}}(K_3) &= \delta(z_1 - z_2) \otimes K_3|_{z_1=z_2} \\
&\quad + \delta(z_2 - z_3) \otimes K_3|_{z_2=z_3} \\
&\quad + \delta(z_1 - z_3) \otimes K_3|_{z_1=z_3}
\end{align*}

Apply again:
\begin{align*}
d_{\text{extend}}^2(K_3) &= \delta(z_1 - z_2) \wedge \delta(z_2 - z_3) \otimes 
K_3|_{z_1=z_2=z_3} \\
&\quad + \delta(z_2 - z_3) \wedge \delta(z_1 - z_3) \otimes K_3|_{z_1=z_2=z_3} \\
&\quad + \delta(z_1 - z_3) \wedge \delta(z_1 - z_2) \otimes K_3|_{z_1=z_2=z_3}
\end{align*}

The three-term Arnold relation (applied heuristically to delta functions, cf.\ the caveat in Case~2 above) gives:
\[\delta(z_1 - z_2) \wedge \delta(z_2 - z_3) + \delta(z_2 - z_3) \wedge \delta(z_1 - z_3) + \delta(z_1 - z_3) \wedge \delta(z_1 - z_2) = 0\]
directly, so the three terms in $d_{\text{extend}}^2(K_3)$ sum to zero:
\[\text{term}_1 + \text{term}_2 + \text{term}_3 = 0\]

Hence $d_{\text{extend}}^2(K_3) = 0$.
\end{example}

\subsection{Low-degree explicit computations}

\begin{example}[Cobar of linear coalgebra through degree 5]
\label{ex:cobar-linear-complete}

Let $\mathcal{C} = T^c_{\text{ch}}(V)$ be the cofree coalgebra on $V = \text{span}\{v\}$ 
with $|v| = h$. The comultiplication is:
\[\Delta(v^n) = \sum_{k=0}^n \binom{n}{k} v^k \otimes v^{n-k}\]

\emph{Cobar complex.}
\[\Omega^{\text{ch}}(T^c_{\text{ch}}(V)) = \text{Free}_{\text{ch}}(s^{-1}V^{\otimes n} 
: n \geq 1)\]

\emph{Generators.} $s^{-1}v, s^{-1}v^2, s^{-1}v^3, s^{-1}v^4, s^{-1}v^5, \ldots$ 
in degrees $h-1, 2h-1, 3h-1, 4h-1, 5h-1, \ldots$ respectively.

\emph{Differential formulas.}

\emph{Degree 1 (h-1):}
\[d(s^{-1}v) = 0\]
(Primitive element, no coproduct.)

\emph{Degree 2 (2h-1):}
The cobar differential uses the \emph{reduced} coproduct $\bar{\Delta}$, which excludes the counit terms:
\begin{align*}
d(s^{-1}v^2) &= -\bar{\Delta}(v^2) = -\sum_{k=1}^{1} \binom{2}{k} (s^{-1}v^k) \cdot (s^{-1}v^{2-k}) \\
&= -\binom{2}{1}(s^{-1}v) \cdot (s^{-1}v) \\
&= -2(s^{-1}v)^2
\end{align*}

\emph{Degree 3 (3h-1):}
\begin{align*}
d(s^{-1}v^3) &= -\bar{\Delta}(v^3) = -\sum_{k=1}^{2} \binom{3}{k} (s^{-1}v^k) \cdot (s^{-1}v^{3-k}) \\
&= -3(s^{-1}v) \cdot (s^{-1}v^2) - 3(s^{-1}v^2) \cdot (s^{-1}v)
\end{align*}

In a commutative setting:
\[d(s^{-1}v^3) = -6(s^{-1}v) \cdot (s^{-1}v^2)\]

\emph{Degree 4 (4h-1):}
\[d(s^{-1}v^4) = -4(s^{-1}v) \cdot (s^{-1}v^3) - 6(s^{-1}v^2) \cdot (s^{-1}v^2)\]

\emph{Degree 5 (5h-1):}
\[d(s^{-1}v^5) = -5(s^{-1}v) \cdot (s^{-1}v^4) - 10(s^{-1}v^2) \cdot (s^{-1}v^3)\]

\emph{General pattern.} For generator $s^{-1}v^n$:
\[d(s^{-1}v^n) = -\sum_{k=1}^{n-1} \binom{n}{k} (s^{-1}v^k) \cdot (s^{-1}v^{n-k})\]

\emph{Geometric interpretation.} These formulas encode how a single insertion
point with ``charge'' $v^n$ splits into two insertion points with charges $v^k$ and
$v^{n-k}$, weighted by binomial coefficients. In CFT, this corresponds to the OPE expansion.

\emph{Cohomology.} Since all generators except $s^{-1}v$ are exact (boundaries 
of products), the cohomology is:
\[H^*(\Omega^{\text{ch}}(T^c_{\text{ch}}(V))) = \text{Free}_{\text{ch}}(s^{-1}v)\]

This recovers the original generator $V$, as expected from bar-cobar inversion.
\end{example}

\begin{example}[Cobar of exterior coalgebra: free fermions]\label{ex:cobar-fermion-complete}

Let $\mathcal{C} = \Lambda^*_{\text{ch}}(V)$ be the chiral exterior coalgebra on 
$V = \text{span}\{\psi\}$ with $|\psi| = \frac{1}{2}$ (fermionic). The comultiplication:
\[\Delta(\psi) = \psi \otimes 1 + 1 \otimes \psi, \quad \Delta(\psi^2) = 0\]
(since $\psi^2 = 0$ by anticommutativity).

\emph{Cobar complex.}
\[\Omega^{\text{ch}}(\Lambda^*_{\text{ch}}(V)) = \text{Free}_{\text{ch}}(s^{-1}\psi)\]

\emph{Generator.} $s^{-1}\psi$ in degree $-\frac{1}{2}$.

\emph{Differential.}
The reduced comultiplication $\bar{\Delta}$ removes the $1 \otimes \psi + \psi \otimes 1$ 
term. For the reduced coproduct:
\[\bar{\Delta}(\psi) = 0\]

Therefore:
\[d(s^{-1}\psi) = 0\]

\emph{Cohomology.}
\[H^*(\Omega^{\text{ch}}(\Lambda^*_{\text{ch}}(V))) = \text{Free}_{\text{ch}}(s^{-1}\psi)\]

The desuspension $s^{-1}$ converts the fermionic generator $\psi$ (with 
anticommuting multiplication) into a bosonic generator $s^{-1}\psi$ (with commuting 
multiplication in the free algebra).

\emph{Physical interpretation.} This is the \emph{Koszul duality} of free fermions (not to be confused with the boson-fermion correspondence/bosonization, which identifies $\mathcal{F} \cong V_{\mathbb{Z}}$ as a lattice vertex algebra).
The cobar construction converts fermionic generators $\psi$ into bosonic generators $\phi = s^{-1}\psi$ via desuspension.
\end{example}

\begin{example}[Free fermion to beta-gamma via bar-cobar]
\label{ex:fermion-betagamma-bar-cobar}

\emph{The Koszul duality chain.}
\[\text{Free fermion algebra } \mathcal{F} \xrightarrow{\text{bar}} \text{Exterior coalgebra }
\bar{B}(\mathcal{F}) \xrightarrow{(-)^\vee} \beta\gamma \text{ system}\]
(The second arrow is linear duality of the coalgebra, yielding the Koszul dual \emph{algebra}~$\mathcal{F}^! = \bar{B}(\mathcal{F})^\vee$.  The cobar construction $\Omega(\bar{B}(\mathcal{F}))$ would instead recover~$\mathcal{F}$ itself by bar-cobar inversion.)

\emph{Explicit construction.}

\begin{theorem}[Fermion-boson Koszul duality; \ClaimStatusProvedHere]\label{thm:fermion-boson-koszul}

\smallskip\noindent
\textup{[Regime: quadratic
\textup{(}Convention~\textup{\ref{conv:regime-tags}}\textup{)}.]}
The $\beta\gamma$ system is the \emph{Koszul dual} of free fermions.
This is the chiral analog of the classical
$\mathrm{Sym}(V) \leftrightarrow \Lambda(V^*)$ Koszul duality
(see Part~II for the complete bar-cobar computation).

The Koszul duality correspondence exchanges:
\begin{enumerate}
\item \emph{Relations}: anticommuting fields $\{\psi, \psi\} = 0$ $\leftrightarrow$ symplectic bosons $[\beta,\gamma] = 1$; exterior relation $\psi \boxtimes \psi = 0$ $\leftrightarrow$ symplectic pairing $\langle \beta, \gamma \rangle = \frac{1}{z_1-z_2}$.

\item \emph{Algebra structure}: exterior algebra $\Lambda^*(\psi)$ $\leftrightarrow$ polynomial-type algebra; bar complex $\bar{B}(\mathcal{F}) = \Lambda^*(\psi, \partial\psi, \ldots)$ $\leftrightarrow$ $\bar{B}(\beta\gamma)$ with symplectic differential.

\item \emph{Statistics}: fermionic $\leftrightarrow$ bosonic.
\end{enumerate}
\end{theorem}

\begin{proof}
The free fermion algebra $\mathcal{F} = \Lambda^{\mathrm{ch}}(V)$ is generated by $V$ with the exterior (anticommutative) chiral product.  By the classical Koszul duality $\Lambda(V)^! = \mathrm{Sym}(V^*)$ (Loday--Vallette~\cite{LV12}, Theorem~3.2.1), the chiral Koszul dual is $\mathcal{F}^! = \mathrm{Sym}^{\mathrm{ch}}(V^*)$, the commutative chiral algebra on $V^*$ --- which is the $\beta\gamma$ system with $\beta \in V^*$, $\gamma \in V$.  The complete bar-cobar computation verifying the Koszul property (acyclicity of $B(\mathcal{F}) \otimes_\tau \mathcal{F}^!$) is carried out in Part~II.
\end{proof}

\emph{Propagator}: The bosonic $\beta\gamma$ system has propagator:
\[\langle \beta(z) \gamma(w) \rangle = \frac{1}{z - w}\]

This matches the fermion two-point function via Koszul duality (not to be confused with bosonization, which is a distinct equivalence $\mathcal{F} \cong V_{\mathbb{Z}}$).
\end{example}

\begin{example}[Cobar \texorpdfstring{$A_\infty$}{A-infinity} operations: explicit formulas through \texorpdfstring{$n_5$}{n5}]
\label{ex:cobar-ainfty-n5}

The cobar construction carries a canonical $A_\infty$ structure. We compute the 
first five operations explicitly.

\emph{Operation $n_1$: The differential}
\[n_1 = d_{\text{cobar}}: \Omega^n(\mathcal{C}) \to \Omega^{n+1}(\mathcal{C})\]
(Already computed above.)

\emph{Operation $n_2$: Convolution product}
\[n_2: \Omega^p(\mathcal{C}) \otimes \Omega^q(\mathcal{C}) \to \Omega^{p+q}(\mathcal{C})\]
(In cohomological grading, $m_k$ has degree $2-k$; for $k=2$, degree $0$: $p+q \mapsto p+q$.)

\emph{Formula.} For integration kernels $K_1, K_2$:
\[(n_2(K_1, K_2))(z_1, \ldots, z_{p+q-1}) = \int_X K_1(z_1, \ldots, z_p; w) \cdot 
K_2(w, z_{p+1}, \ldots, z_{p+q-1}) \, dw\]

\emph{Geometric interpretation.} Glue two configuration spaces at a common point
$w$, then integrate over $w$.

\emph{Sign.} $(-1)^{|K_1| \cdot |K_2|}$ from Koszul rule.

\emph{Example.} For $K_1 = \frac{1}{z_1 - w}$, $K_2 = \frac{1}{w - z_2}$, using partial fractions:
\begin{align*}
n_2(K_1, K_2)(z_1, z_2) &= \oint \frac{1}{z_1 - w} \cdot \frac{1}{w - z_2} \, dw \\
&= \frac{1}{z_1 - z_2}\oint \left[\frac{1}{w - z_2} - \frac{1}{w - z_1}\right] dw \\
&= \frac{2\pi i}{z_1 - z_2} \quad \text{(residue at } w = z_2\text{)}
\end{align*}
This reproduces the expected propagator $1/(z_1 - z_2)$ (up to normalization $2\pi i$).

\emph{Operation $n_3$: Triple propagator}
\[n_3: \Omega^{p_1}(\mathcal{C}) \otimes \Omega^{p_2}(\mathcal{C}) \otimes 
\Omega^{p_3}(\mathcal{C}) \to \Omega^{p_1+p_2+p_3-2}(\mathcal{C})\]

\emph{Formula.}
\[(n_3(K_1, K_2, K_3))(z_1, \ldots, z_N) = \int_{X \times X} K_1(\ldots; w_1) \cdot 
K_2(w_1, \ldots; w_2) \cdot K_3(w_2, \ldots) \, dw_1 dw_2\]

\emph{Geometric interpretation.} Glue three configuration spaces in a chain,
then integrate over the two gluing points.

\emph{Operation $n_4$: Four-point function}
\[n_4: \bigotimes_{i=1}^4 \Omega^{p_i}(\mathcal{C}) \to \Omega^{\sum p_i - 3}(\mathcal{C})\]

\emph{Formula.} Similar, but integrate over three intermediate points $w_1, w_2, w_3$.

\emph{Operation $n_5$: Five-point function}
\[n_5: \bigotimes_{i=1}^5 \Omega^{p_i}(\mathcal{C}) \to \Omega^{\sum p_i - 4}(\mathcal{C})\]

\emph{General pattern.}
\[n_k: \bigotimes_{i=1}^k \Omega^{p_i}(\mathcal{C}) \to \Omega^{\sum p_i - (k-2)}(\mathcal{C})\]

\emph{Geometric realization.} Integrate over the moduli space $\overline{M}_{0,k+1}$
of stable curves:
\[n_k(K_1, \ldots, K_k) = \int_{\overline{M}_{0,k+1}} K_1 \wedge \cdots \wedge K_k 
\wedge \omega_{0,k+1}\]

\emph{Physical interpretation.} The operation $n_k$ computes $k$-point correlation
functions in CFT. The integration over $\overline{M}_{0,k+1}$ sums over all Feynman
diagrams (tree-level for genus 0).

\emph{$A_\infty$ relations.} These operations satisfy:
\[\sum_{i+j=n+1} \sum_{k} (-1)^{\epsilon} n_i(\text{id}^{\otimes k} \otimes n_j 
\otimes \text{id}^{\otimes (n-k-j)}) = 0\]

This encodes associativity up to homotopy, with $n_3$ measuring the failure of 
$n_2$ to be associative, $n_4$ measuring the failure of $n_3$ to be coherent, etc.
\end{example}

\subsection{Physical interpretation: on-shell propagator and Feynman-rule templates}

\begin{conjecture}[Cobar elements as on-shell propagator templates; \ClaimStatusHeuristic]\label{conj:cobar-physical}
Elements of the cobar complex $\Omega^{\text{ch}}(\mathcal{C})$ should be read as
\emph{algebraic shadow data for on-shell propagators} in the sense of quantum
field theory.

\emph{Precise statement.} For a chiral coalgebra $\mathcal{C}$ corresponding
to a 2d CFT, elements $K \in \Omega^n(\mathcal{C})$ are distributions satisfying:
\begin{enumerate}
\item \emph{Ultraviolet behavior:} Singularities along diagonals $\{z_i = z_j\}$ 
encode short-distance behavior (UV divergences).
\item \emph{On-shell condition:} The cobar differential $d_{\text{cobar}}(K) = 0$ 
should model the equations of motion (e.g., $\Box \phi = 0$ for free fields).
\item \emph{S-matrix elements:} The cohomology $H^*(\Omega^{\text{ch}}(\mathcal{C}))$ 
should model physical on-shell scattering amplitudes.
\end{enumerate}
\end{conjecture}

\begin{remark}[Physical motivation]
\emph{Step 1: Cobar as Green's-function template}

A propagator $G(z,w)$ in QFT is a Green's function satisfying:
\[(\Box_z - m^2) G(z,w) = \delta^{(2)}(z - w)\]

This is the Green's-function template in which $G$ extends across the diagonal
$z = w$ as a distribution with a delta function singularity. In the
conjectural cobar/QFT dictionary this is modeled by:
\[d_{\text{extend}}(G) = \delta(z - w)\]

\emph{Step 2: Cobar differential as equations-of-motion template}

For a field $\phi$ satisfying equations of motion $\Box \phi = 0$, the propagator 
$G$ satisfies:
\[d_{\text{cobar}}(G) = 0\]

This is the template for the \emph{on-shell condition}. Elements in the
cohomology $H^*(\Omega^{\text{ch}})$ should therefore be read as algebraic
shadows of on-shell propagators.

\emph{Step 3: $A_\infty$ operations as Feynman-rule template}

The operation $n_k$ in the cobar $A_\infty$ structure should model tree-level
$k$-point correlation
functions:
\[\langle \phi(z_1) \cdots \phi(z_k) \rangle = n_k(G, \ldots, G)(z_1, \ldots, z_k)\]

The $A_\infty$ relations encode (all at genus zero, hence tree-level):
\begin{itemize}
\item $n_2$ = binary vertex (standard product)
\item $n_3$ = ternary vertex (measures failure of strict associativity)
\item $n_k$ = $k$-ary vertex (higher associahedra corrections)
\end{itemize}
Loop corrections (genus $g \geq 1$) arise from the higher-genus bar complex, not from higher $n_k$ at genus zero.

This gives the conjectural algebraic template for genus-zero Feynman rules.
\end{remark}

\begin{remark}[Scope]
Conjecture~\ref{conj:cobar-physical} is tagged \ClaimStatusHeuristic{} because the identification of cobar elements with on-shell propagators requires external physics input (equations of motion, path integral measure) that lies outside the algebraic framework of this monograph.

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~VII (physics-dictionary).
The conjecture treats cobar complex elements as algebraic shadow data for
QFT on-shell propagators, with the $A_\infty$ operations furnishing the
genus-zero Feynman-rule template.
\end{remark}

\begin{example}[Free scalar field: complete cobar analysis]\label{ex:free-scalar-cobar}

Consider the free scalar field with action:
\[S = \int \frac{1}{2} (\partial \phi)^2 dz \wedge d\bar{z}\]

\emph{Equation of motion.} $\Box \phi = 0$

\emph{Propagator.}
\[G(z,w) = -\frac{1}{2\pi} \log|z - w|^2\]

This satisfies:
\[\Box_z G(z,w) = \delta^{(2)}(z - w)\]

\emph{Cobar interpretation.}
\[d_{\text{extend}}(G) = \delta(z - w)\]

\emph{Two-point function.} Already on-shell, so:
\[\langle \phi(z_1) \phi(z_2) \rangle = G(z_1, z_2) = -\frac{1}{2\pi} \log|z_1 - z_2|^2\]

\emph{Four-point function.} Computed using $n_4$:
\begin{align*}
\langle \phi(z_1) \phi(z_2) \phi(z_3) \phi(z_4) \rangle &= n_4(G, G, G, G) \\
&= \int_{X \times X} G(z_1, w_1) G(w_1, z_2) G(z_3, w_2) G(w_2, z_4) \,
dw_1 \, dw_2
\end{align*}

This is the Wick contraction formula. The cobar $A_\infty$ structure
automatically implements Wick's theorem.
\end{example}

\begin{remark}[CFT vertex operators from cobar]\label{rem:vertex-operators-cobar}
In conformal field theory, vertex operators $V_\alpha(z)$ create states $|\alpha\rangle$ 
at position $z$. These correspond to cobar elements:
\[V_\alpha \leftrightarrow K_\alpha \in \Omega^1(\mathcal{C})\]

The OPE of vertex operators:
\[V_\alpha(z) V_\beta(w) \sim \sum_\gamma \frac{C_{\alpha\beta}^\gamma}{(z-w)^{h_\gamma - h_\alpha - h_\beta}} V_\gamma(w)\]

corresponds to the cobar product:
\[n_2(K_\alpha, K_\beta) = \sum_\gamma C_{\alpha\beta}^\gamma K_\gamma\]

The structure constants $C_{\alpha\beta}^\gamma$ are precisely the cobar $A_\infty$ 
structure constants.

The cobar construction thus provides a geometric derivation
of the OPE algebra in CFT.
\end{remark}

\subsection{Verdier duality on bar and cobar}


\begin{theorem}[Bar-cobar Verdier; \ClaimStatusProvedHere]\label{thm:bar-cobar-verdier}
\label{thm:verdier-bar-cobar}
\index{Verdier duality!bar-cobar|textbf}
\textup{[Regime: quadratic, genus-$0$
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

There is a perfect pairing:
\[\langle \cdot, \cdot \rangle: \bar{B}^{\text{ch}}_n(\mathcal{A}) \otimes 
\Omega^{\text{ch}}_n(\mathcal{C}) \to \mathbb{C}\]

given by:
\[\langle \omega_{\text{bar}}, K_{\text{cobar}} \rangle = \int_{\overline{C}_n(X)} 
\omega_{\text{bar}} \wedge \iota^* K_{\text{cobar}}\]

where:
\begin{itemize}
\item $\omega_{\text{bar}} \in \Gamma(\overline{C}_n(X), \mathcal{A}^{\boxtimes n} 
\otimes \Omega^*_{\log})$ is a bar element (logarithmic form on compactified space)
\item $K_{\text{cobar}} \in \mathcal{D}'(C_n(X), \mathcal{C}^{\boxtimes n})$ is 
a cobar element (distribution on open space)
\item $\iota: C_n(X) \hookrightarrow \overline{C}_n(X)$ is the inclusion of the 
open configuration space
\item The integration is well-defined because logarithmic forms pair with distributions
\end{itemize}

\emph{Properties of the pairing.}
\begin{enumerate}
\item \emph{Perfect pairing:} Non-degenerate in both arguments (by Lemma~\ref{lem:bar-holonomicity}: each graded piece is a holonomic $\mathcal{D}$-module on $\overline{C}_n(X)$, hence has finite-dimensional stalks, and Verdier duality for holonomic $\mathcal{D}$-modules is an involution~\cite{KS90})
\item \emph{Differential compatibility:} $\langle d_{\text{bar}}\omega, K \rangle 
= -\langle \omega, d_{\text{cobar}}K \rangle$ (graded Leibniz rule)
\item \emph{Residue-distribution duality:} $\langle \text{Res}_{D}[\omega], 
\delta_D \rangle = 1$ for any divisor $D$
\item \emph{Verdier duality:} This realizes $\Omega^{\text{ch}}(\mathcal{C}) 
\simeq \mathbb{D}(\bar{B}^{\text{ch}}(\mathcal{A}^!))$
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Step 1: Well-definedness of the pairing}

Logarithmic forms on $\overline{C}_n(X)$ restrict to distributional 
forms on $C_n(X)$. Explicitly, near a divisor $D = \{z_i = z_j\}$ with local 
coordinate $\epsilon = z_i - z_j$:

Logarithmic form: $\omega = \frac{d\epsilon}{\epsilon} \wedge (\text{smooth forms})$

Restriction to $C_n(X)$: $\iota^*\omega$ has a pole at $\epsilon = 0$, hence is 
a distribution on $C_n(X) = \overline{C}_n(X) \setminus D$.

The pairing integrates this distribution against the cobar distribution:
\[\langle \omega, K \rangle = \int_{\overline{C}_n(X)} \omega \wedge K\]

This is well-defined by the theory of currents (de Rham's theorem on distributions).

\emph{Step 2: Differential compatibility}

We verify:
\[\langle d_{\text{bar}}\omega, K \rangle = -\langle \omega, d_{\text{cobar}}K \rangle\]

At the level of $\mathcal{D}$-modules on $\overline{C}_n(X)$, the bar and cobar differentials are flat connections (the bar complex is a complex of holonomic $\mathcal{D}$-modules by Lemma~\ref{lem:bar-holonomicity}).  Verdier duality is an exact contravariant involution on $D^b_{\mathrm{hol}}(\mathcal{D}_{\overline{C}_n(X)})$ that sends a flat connection $\nabla$ to the adjoint connection $\nabla^\dagger$ (see~\cite{KS90}, Chapter~4).

We make the adjoint identity explicit.  For a holonomic $\mathcal{D}$-module $\mathcal{M}$ on a smooth variety $Y$ of dimension~$d$, the Verdier dual is $\mathbb{D}\mathcal{M} = R\mathcal{H}\!\mathit{om}_{\mathcal{D}_Y}(\mathcal{M}, \mathcal{D}_Y \otimes \Omega_Y^{-1})[d]$.  When $\mathcal{M}$ carries a flat connection $\nabla \colon \mathcal{M} \to \mathcal{M} \otimes \Omega^1_Y$, sections $m^* \in \mathbb{D}\mathcal{M}$ inherit the adjoint connection $\nabla^\dagger$ defined by
\[\langle \nabla^\dagger m^*,\, m \rangle \;=\; -\,\langle m^*,\, \nabla m \rangle\]
for all local sections $m \in \mathcal{M}$, where $\langle -,- \rangle$ is the canonical pairing $\mathbb{D}\mathcal{M} \otimes \mathcal{M} \to \omega_Y$.  This is the unique connection on $\mathbb{D}\mathcal{M}$ making the pairing flat, i.e., satisfying $d\langle m^*, m\rangle = \langle \nabla^\dagger m^*, m\rangle + \langle m^*, \nabla m\rangle = 0$.

Applying this to $Y = \overline{C}_n(X)$, $\mathcal{M} = \bar{B}^{\mathrm{ch}}_n(\mathcal{A})$ with $\nabla = d_{\mathrm{bar}}$, and $\mathbb{D}\mathcal{M} = \Omega^{\mathrm{ch}}_n(\mathcal{A}^!)$ (by item~(3) of the theorem; we verify this pairing in Step~3 below; the present step is logically independent and uses only the formal structure of the adjoint connection on holonomic $\mathcal{D}$-modules), one obtains $d_{\mathrm{cobar}} = d_{\mathrm{bar}}^\dagger$ as the Verdier-adjoint connection.  The differential compatibility
\[\langle d_{\text{bar}}\omega, K \rangle = -\langle \omega, d_{\text{cobar}}K \rangle\]
therefore holds by the flatness of the canonical pairing on holonomic $\mathcal{D}$-modules, without requiring a component-by-component Stokes argument.

\emph{Step 3: Residue-distribution pairing}

The fundamental pairing:
\[\langle \eta_{ij}, \delta(z_i - z_j) \rangle = \int \frac{dz_i - dz_j}{z_i - z_j} 
\wedge \delta(z_i - z_j) = 1\]

where $\eta_{ij} = \frac{dz_i - dz_j}{z_i - z_j}$ is the logarithmic 1-form along 
$D_{ij}$.

\emph{Proof of identity.} Regularize the delta function:
\[\delta_\epsilon(z) = \frac{1}{\pi \epsilon^2} e^{-|z|^2/\epsilon^2}\]

Then:
\begin{align*}
\langle \eta_{ij}, \delta_\epsilon \rangle &= \int \frac{dz_i - dz_j}{z_i - z_j} 
\wedge \delta_\epsilon(z_i - z_j) \\
&= \int_{|w| < \infty} \frac{dw}{w} \wedge \delta_\epsilon(w) \\
&= \lim_{\epsilon \to 0} \int_{|w| < \infty} \frac{dw}{w} \wedge \frac{1}{\pi \epsilon^2} 
e^{-|w|^2/\epsilon^2}
\end{align*}

Change variables $u = w/\epsilon$:
\begin{align*}
&= \lim_{\epsilon \to 0} \int \frac{d(\epsilon u)}{\epsilon u} \wedge \frac{1}{\pi} 
e^{-|u|^2} \\
&= \int \frac{du}{u} \wedge \frac{1}{\pi} e^{-|u|^2} \\
&= \frac{1}{2\pi i} \oint_{|u|=1} \frac{du}{u} \quad \text{(by residue theorem)} \\
&= 1
\end{align*}

This confirms the perfect pairing between residues and delta functions.

\emph{Step 4: Verdier duality realization}

The pairing establishes an isomorphism:
\[\Omega^{\text{ch}}(\mathcal{C}) \xrightarrow{\sim} \mathbb{D}(\bar{B}^{\text{ch}}(\mathcal{A}^!))\]

where $\mathbb{D}$ is the Verdier dualizing functor.

\emph{Non-degeneracy.}
At bar degree~$n = 1$, Step~3 establishes the fundamental pairing
$\langle \eta_{ij}, \delta(z_i - z_j) \rangle = 1$.  For $n > 1$,
non-degeneracy follows by induction using the coalgebra structure: the
comultiplication on $\bar{B}^n$ decomposes an $n$-point integrand into
products of lower-point integrands via the K\"unneth formula on the
FM boundary strata $\partial\overline{C}_n(X) \cong
\coprod_{|S|=k} \overline{C}_k(X) \times \overline{C}_{n-k+1}(X)$.
The induced pairing at degree~$n$ is the tensor product of
pairings at degrees~$k$ and~$n{-}k{+}1$, which are non-degenerate
by the induction hypothesis.  Therefore the map is an isomorphism
at each bar degree.

\emph{Geometric meaning.}
\begin{itemize}
\item Bar = cohomology with compact support (logarithmic forms on $\overline{C}_n$)
\item Cobar = homology (distributional cycles on $C_n$)
\item Pairing = Poincar\'e duality between cohomology and homology
\end{itemize}

This completes the proof.
\end{proof}

\begin{corollary}[Bar-cobar mutual inverses; \ClaimStatusProvedHere]\label{cor:bar-cobar-inverse}
\index{bar-cobar inversion|textbf}
\index{quasi-isomorphism!bar-cobar}
Let $\mathcal{A}$ be an augmented chiral algebra on a smooth curve $X$,
valued in holonomic $\mathcal{D}$-modules
(Convention~\ref{subsec:ambient-category}), and let $\mathcal{C}$ be an
augmented chiral coalgebra.  Assume:
\begin{enumerate}[label=(\roman*)]
\item $\mathcal{A}$ is \emph{chiral Koszul}: the bar complex
  $\bar{B}^{\mathrm{ch}}(\mathcal{A})$ has cohomology concentrated in a
  single degree (Definition~\ref{def:chiral-koszul-pair});
\item \emph{Conilpotence or completion}: either
  $\bar{B}^{\mathrm{ch}}(\mathcal{A})$ is conilpotent, or $\mathcal{A}$
  is complete with respect to its augmentation ideal
  (\S\ref{sec:i-adic-completion}).
\end{enumerate}
Then the bar and cobar functors are mutually quasi-inverse:
\[\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A})) \xrightarrow{\sim} \mathcal{A}\]
\[\bar{B}^{\mathrm{ch}}(\Omega^{\mathrm{ch}}(\mathcal{C})) \xrightarrow{\sim} \mathcal{C}\]

The quasi-isomorphisms are induced by the Verdier pairing
(Theorem~\ref{thm:bar-cobar-verdier}).
\end{corollary}

\begin{proof}
Consider the coradical filtration $F_\bullet$ on
$\bar{B}^{\mathrm{ch}}(\mathcal{A})$, where $F_n$ is spanned by elements
of tensor degree $\leq n$.  The associated spectral sequence has
$E_1^{p,q} = H^{p+q}(\mathrm{gr}_p\, \Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A})))$.

Under hypothesis (i), the Koszulity condition ensures that $E_2$ collapses:
the only nonzero column is $p = 0$, where it gives $\mathcal{A}$.

Convergence of the spectral sequence is guaranteed by hypothesis (ii):
conilpotence ensures the filtration is exhaustive with finite-length iterated
coproducts, so the cobar differential involves only finite sums.  In the
completed regime, convergence follows from the completeness of the
$I$-adic topology.

The unit $\eta: \mathcal{A} \to \Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A}))$
is induced by the Verdier pairing (Theorem~\ref{thm:bar-cobar-verdier})
and is a quasi-isomorphism by the spectral sequence argument.
The counit argument is dual.
\end{proof}

\begin{proposition}[Explicit cobar-bar augmentation; \ClaimStatusProvedHere]
\label{prop:cobar-bar-augmentation}
\index{augmentation map!cobar-bar|textbf}
\index{quasi-isomorphism!explicit chain map}
Let $\mathcal{A}$ be an augmented chiral algebra satisfying the
hypotheses of Corollary~\ref{cor:bar-cobar-inverse}.
The \emph{augmentation map}
$\varepsilon\colon
\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A}))
\to \mathcal{A}$
is constructed as follows.

\emph{On generators.}
By Theorem~\ref{thm:cobar-free},
$\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A}))
= \mathrm{Free}_{\mathrm{ch}}(s^{-1}\overline{B})$
where $\overline{B} = \bigoplus_{n \geq 1}
\bar{B}^{\mathrm{ch}}_n(\mathcal{A})$ is the coaugmentation
coideal of the bar coalgebra.
Define $\varepsilon$ on generators $s^{-1}\overline{B}$ as the
composite
\begin{equation}\label{eq:augmentation-on-generators}
s^{-1}\overline{B}
\;\xrightarrow{s^{-1}\pi_1}\;
s^{-1}\bar{B}^{\mathrm{ch}}_1(\mathcal{A})
\;\xrightarrow[\sim]{}\;
\bar{\mathcal{A}}
\;\hookrightarrow\; \mathcal{A},
\end{equation}
where $\pi_1$ projects to bar degree~$1$ and
$s^{-1}\bar{B}^{\mathrm{ch}}_1(\mathcal{A})
\cong \bar{\mathcal{A}}$
uses the suspension identification
$\bar{B}^{\mathrm{ch}}_1 = s\bar{\mathcal{A}}$.
In particular, $\varepsilon$ \emph{kills} all generators from bar
degree~$\geq 2$.

\emph{Extension.}
By the universal property of the free chiral algebra
(Theorem~\ref{thm:cobar-free}), the restriction
\eqref{eq:augmentation-on-generators} extends uniquely to a
chiral algebra morphism
$\varepsilon\colon
\mathrm{Free}_{\mathrm{ch}}(s^{-1}\overline{B}) \to \mathcal{A}$.

\emph{Low-arity formulas.}
On generators:
\begin{align}
\varepsilon(s^{-1}[s\bar{a}]) &= \bar{a}
  &&\text{(inclusion of the augmentation ideal),}
  \label{eq:aug-arity-1} \\
\varepsilon(s^{-1}[s\bar{a}_1 \mid s\bar{a}_2]) &= 0
  &&\text{(projection kills bar degree $\geq 2$).}
  \label{eq:aug-arity-2-gen}
\end{align}
On products of generators (by the algebra map property):
\begin{equation}\label{eq:aug-product}
\varepsilon\bigl(s^{-1}[s\bar{a}_1]
  \cdot s^{-1}[s\bar{a}_2]\bigr)
= \bar{a}_{1\,(0)}\bar{a}_2
\qquad\text{(the zeroth chiral product).}
\end{equation}
Here $s^{-1}[s\bar{a}_1 \mid s\bar{a}_2]$ is a \emph{single
generator} from bar degree~$2$ (which $\varepsilon$ kills),
while $s^{-1}[s\bar{a}_1] \cdot s^{-1}[s\bar{a}_2]$ is a
\emph{product} of two generators from bar degree~$1$ (which
$\varepsilon$ evaluates via the chiral multiplication
$\bar{a}_{1\,(0)}\bar{a}_2$).
\end{proposition}

\begin{proof}
\emph{Step~1: Chain map property.}
We verify $\varepsilon \circ d_\Omega = 0$
(the target differential vanishes since $\mathcal{A}$ is a strict
chiral algebra).  Since $\varepsilon$ is an algebra morphism and
$d_\Omega$ is a derivation
(Theorem~\ref{thm:cobar-free}), it suffices to check on generators
$s^{-1} b$ for $b \in \bar{B}^{\mathrm{ch}}_n(\mathcal{A})$.

The cobar differential on generators decomposes as
(Theorem~\ref{thm:cobar-diff-geom}):
\[
d_\Omega(s^{-1} b)
\;=\; \pm\, s^{-1}(d_{\mathrm{bar}}\, b)
\;+\; \sum \pm\, s^{-1} b' \cdot s^{-1} b''
\]
where $d_{\mathrm{bar}}$ is the bar differential and
$\bar{\Delta}(b) = \sum b' \otimes b''$ is the reduced coproduct
(signs determined by the Koszul rule for desuspension).

\emph{Bar degree $n=1$:}
$b = [s\bar{a}] \in \bar{B}^{\mathrm{ch}}_1$.
Then $d_{\mathrm{bar}}\, b = 0$ (bar degree~$1$ elements are
primitives annihilated by the differential) and
$\bar{\Delta}(b) = 0$ (no non-trivial decomposition).
Hence $d_\Omega(s^{-1}[s\bar{a}]) = 0$ and $\varepsilon(0) = 0$.

\emph{Bar degree $n=2$:}
$b = [s\bar{a}_1 \mid s\bar{a}_2] \in \bar{B}^{\mathrm{ch}}_2$.
The bar differential yields
$d_{\mathrm{bar}}\, b
= \pm\, [s(\bar{a}_{1\,(0)}\bar{a}_2)]
\in \bar{B}^{\mathrm{ch}}_1$
(residue extraction of the OPE), while the coproduct gives
$\bar{\Delta}(b) = [s\bar{a}_1] \otimes [s\bar{a}_2]$
(deconcatenation).
Applying $\varepsilon$:
\begin{align*}
\varepsilon(d_\Omega(s^{-1} b))
&= \pm\, \varepsilon(s^{-1}[s(\bar{a}_{1\,(0)}\bar{a}_2)])
  \;+\; \pm\, \varepsilon(s^{-1}[s\bar{a}_1]
    \cdot s^{-1}[s\bar{a}_2]) \\
&= \pm\, \bar{a}_{1\,(0)}\bar{a}_2
  \;\pm\; \bar{a}_{1\,(0)}\bar{a}_2
\;=\; 0,
\end{align*}
where the two signs are opposite by the Maurer--Cartan equation
for the universal twisting morphism
$\tau = \varepsilon|_{s^{-1}\overline{B}}\colon
\bar{B}^{\mathrm{ch}}(\mathcal{A}) \to \mathcal{A}$
(\cite[\S2.2, Proposition~2.2.6]{LV12}).

\emph{Bar degree $n \geq 3$:}
$d_{\mathrm{bar}}\, b$ lies in bar degree $n{-}1 \geq 2$, which
$\varepsilon$ kills.  Each summand $s^{-1}b' \cdot s^{-1}b''$ in the
coproduct decomposition has at least one factor of bar
degree~$\geq 2$, so $\varepsilon$ kills it.
Hence $\varepsilon(d_\Omega(s^{-1} b)) = 0$.

\emph{Step~2: Quasi-isomorphism.}
Filter $\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A}))$
by word length in the free algebra:
\[
F_p = \bigoplus_{k \leq p}
\mathrm{Free}_{\mathrm{ch}}^{(k)}(s^{-1}\overline{B}),
\]
where $\mathrm{Free}_{\mathrm{ch}}^{(k)}$ is the component of
word length~$k$.
On the associated graded, the differential reduces to the
\emph{linearized} part $d_{\mathrm{lin}} = s^{-1} d_{\mathrm{bar}}\, s$,
acting within each copy of $s^{-1}\overline{B}$.
The $E_1$ page is:
\[
E_1^{p,q}
= \mathrm{Free}_{\mathrm{ch}}^{(p)}\!\bigl(
  s^{-1} H^q(\bar{B}^{\mathrm{ch}}(\mathcal{A}))
\bigr).
\]
The Koszul hypothesis forces the bar coalgebra cohomology
$H^*(\bar{B}^{\mathrm{ch}}(\mathcal{A}))$
to be concentrated in a single cohomological degree
(Convention~\ref{conv:bar-coalgebra-identity}).
Therefore $E_1^{p,q} = 0$ for $q \neq 0$, so $d_1 = 0$ and
$E_2 = E_1 = E_\infty$.

The augmentation $\varepsilon$ induces on $E_\infty$:
\[
\varepsilon_*\colon E_\infty^{1,0}
= s^{-1}H^0(\bar{B}^{\mathrm{ch}}_1) = \bar{\mathcal{A}}
\;\xrightarrow{\;\sim\;}\; \mathcal{A},
\qquad
\varepsilon_*|_{E_\infty^{p,0}} = 0 \;\text{for } p \geq 2.
\]
Convergence of the spectral sequence (by conilpotence or
completeness, as in
Corollary~\ref{cor:bar-cobar-inverse})
yields
$H^*(\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A})))
\cong \mathcal{A}$,
and $\varepsilon$ realizes this isomorphism at the cochain level.
\end{proof}

\begin{remark}[The chiral bar-cobar adjunction via twisting morphisms]
\label{rem:chiral-adjunction-via-tw}
\index{bar-cobar adjunction!via twisting morphisms!chiral}
\index{twisting morphism!chiral universal}
The projection
$\pi = \varepsilon|_{s^{-1}\overline{B}}\colon
\barB^{\mathrm{ch}}(\cA) \to \cA$
is the chiral universal twisting morphism
(Proposition~\ref{prop:universal-twisting-adjunction}(i),
Definition~\ref{def:chiral-twisting-datum}).
By the two universal properties
(Proposition~\ref{prop:universal-twisting-adjunction}(i)--(ii)),
the \emph{chiral bar-cobar adjunction} is:
\begin{equation}\label{eq:chiral-tw-adjunction}
\mathrm{Hom}_{\mathrm{dg\,CoAlg}}(\mathcal{C},\,
  \barB^{\mathrm{ch}}(\cA))
\;\cong\;
\mathrm{Tw}^{\mathrm{ch}}(\mathcal{C},\, \cA)
\;\cong\;
\mathrm{Hom}_{\mathrm{dg\,Alg}}(\Omega^{\mathrm{ch}}(\mathcal{C}),\,
  \cA).
\end{equation}
On the Koszul locus,
$\barB^{\mathrm{ch}}(\cA) \otimes_\pi \cA \simeq \mathbb{k}$
(Theorem~\ref{thm:fundamental-twisting-morphisms}): unit and counit
are quasi-isomorphisms.
\end{remark}

\begin{example}[Augmentation for \texorpdfstring{$\widehat{\mathfrak{sl}}_2$}{sl2-hat}]
\label{ex:augmentation-sl2}
For the affine Kac--Moody algebra
$\mathcal{A} = V_k(\mathfrak{sl}_2)$ with basis
$\{J^+, J^0, J^-\}$ and OPE
$J^a(z) J^b(w) \sim f^{ab}_c J^c(w)/(z-w)
+ k\,\kappa(J^a, J^b)/(z-w)^2$,
the augmentation acts as:
\begin{align*}
\varepsilon(s^{-1}[sJ^a]) &= J^a
  &&\text{(recovery of generators),} \\
\varepsilon(s^{-1}[sJ^a] \cdot s^{-1}[sJ^b])
&= J^a_{(0)}J^b = f^{ab}_c J^c
  &&\text{(recovery of structure constants).}
\end{align*}
Thus $\varepsilon(s^{-1}[sJ^+] \cdot s^{-1}[sJ^-]) = J^0$
(= $[J^+, J^-] = H$),
confirming that the augmentation recovers the
$\mathfrak{sl}_2$ Lie bracket from the cobar-bar resolution.
\end{example}

\begin{example}[Explicit pairing: two-point function]\label{ex:pairing-two-point}

Consider $n=2$. The bar element is:
\[\omega_{\text{bar}} = a_1(z_1) \otimes a_2(z_2) \otimes \frac{dz_1 - dz_2}{z_1 - z_2}\]

The cobar element is:
\[K_{\text{cobar}} = c_1(z_1) \otimes c_2(z_2) \otimes \delta(z_1 - z_2)\]

The pairing:
\begin{align*}
\langle \omega_{\text{bar}}, K_{\text{cobar}} \rangle &= \int_{\overline{C}_2(X)} 
(a_1 \otimes a_2) \cdot (c_1 \otimes c_2) \wedge \frac{dz_1 - dz_2}{z_1 - z_2} 
\wedge \delta(z_1 - z_2) \\
&= \int_X (a_1 \otimes a_2)(z, z) \cdot (c_1 \otimes c_2)(z, z) \wedge dz \wedge d\bar{z}
\end{align*}

By the residue-distribution identity:
\[\int \frac{dz_1 - dz_2}{z_1 - z_2} \wedge \delta(z_1 - z_2) = 1\]

Therefore:
\[\langle \omega_{\text{bar}}, K_{\text{cobar}} \rangle = \int_X \langle a_1, c_1 
\rangle \cdot \langle a_2, c_2 \rangle \, dz \wedge d\bar{z}\]

This is the two-point correlation function in CFT.
\end{example}

\subsection{Kontsevich formality and chiral bar construction}

\begin{theorem}[Kontsevich formality (1997); \ClaimStatusProvedElsewhere]\label{thm:kontsevich-formality}
\cite{Kon99} For any smooth manifold $M$, there exists an $L_\infty$ 
quasi-isomorphism:
\[\mathcal{U}: T_{\text{poly}}(M) \xrightarrow{\sim} D_{\text{poly}}(M)\]
from polyvector fields to polydifferential operators, given by configuration space integrals:
\[\mathcal{U}_n(\gamma_1, \ldots, \gamma_n) = \sum_{\Gamma \in G_n} w_\Gamma 
\int_{\overline{C}_{n,m}(\mathbb{H})} \omega_\Gamma\]
where $G_n$ = admissible graphs, $w_\Gamma$ = combinatorial weights, and 
$\omega_\Gamma$ involves propagators $d\log(z_i - z_j)$ and angle forms $d\theta_i$.
\end{theorem}

\begin{remark}[Relation to chiral bar construction]\label{rem:kontsevich-chiral}
Kontsevich's formality is the prototype for our construction: replace $\mathbb{R}^d$ with a Riemann surface $X$, polyvector fields with $\mathcal{A}$, $\overline{C}_n(\mathbb{H})$ with $\overline{C}_n(X)$, and $L_\infty$ with curved $A_\infty$.  Both realize a duality (deformation quantization resp.\ Koszul duality) via configuration space integrals.
\end{remark}

\begin{remark}[Costello--Gwilliam factorization algebras]\label{rem:CG-factorization-detailed}
Our construction extends~\cite{CG17}: Vol.~1 develops factorization homology on manifolds, Vol.~2 treats quantum corrections and curved $A_\infty$ in QFT.  We specialize to complex curves (essential for chiral structure) and use configuration geometry rather than the BV formalism.
\end{remark}

\begin{remark}[Cobar summary]
The geometric cobar is Verdier-dual to the bar (Section~\ref{sec:bar-nilpotency}): the three-component differential, nine-term $d^2 = 0$ verification, and Arnold relations all mirror their bar counterparts.
\end{remark}

\subsection{Čech-Alexander complex realization}

\begin{theorem}[Cobar as Čech complex; \ClaimStatusProvedHere]\label{thm:cobar-cech}
The geometric cobar complex is quasi-isomorphic to a Čech-type complex:
\[
\Omega^{\text{ch}}(\mathcal{C}) \simeq \check{C}^{\bullet}(\mathfrak{U}, \mathcal{F}_{\mathcal{C}})
\]
where $\mathfrak{U} = \{U_{\sigma}\}$ is the open cover of $\overline{C}_n(X)$ by coordinate charts and $\mathcal{F}_{\mathcal{C}}$ is the factorization algebra associated to $\mathcal{C}$.
\end{theorem}

\begin{proof}
The factorization algebra $\mathcal{F}_{\mathcal{C}}$ on $X$ is defined by the assignment $U \mapsto \mathcal{F}_{\mathcal{C}}(U) = \Omega(\mathcal{C}|_U)$, with factorization structure maps $\mathcal{F}_{\mathcal{C}}(U_1) \otimes \mathcal{F}_{\mathcal{C}}(U_2) \to \mathcal{F}_{\mathcal{C}}(U_1 \sqcup U_2)$ for disjoint opens, given by the cobar product.  This is a cosheaf on the Ran space $\operatorname{Ran}(X)$, hence in particular a precosheaf on $X$.

\emph{Step 1: Cover and nerve.}
Choose a cover $\mathfrak{U} = \{U_\sigma\}_{\sigma \in S}$ of $X$ by coordinate discs.  The configuration space $C_n(X)$ inherits an open cover $\mathfrak{U}^{(n)} = \{U_{\sigma_1} \times \cdots \times U_{\sigma_n} \cap C_n(X)\}$.  The FM compactification $\overline{C}_n(X)$ is covered by the closures $\overline{U_{\sigma_1} \times \cdots \times U_{\sigma_n}}$ together with boundary coordinate charts at collision strata.  The nerve of this cover computes the Čech complex $\check{C}^\bullet(\mathfrak{U}, \mathcal{F}_{\mathcal{C}})$.

\emph{Step 2: Čech-de Rham comparison.}
On each chart $U_\sigma$, the factorization algebra $\mathcal{F}_{\mathcal{C}}|_{U_\sigma}$ is computed by the cobar complex with local coordinates.  The cobar differential $d_\Omega$ on $U_\sigma$ uses the coproduct $\bar{\Delta}$ of $\mathcal{C}$ together with the local propagator $\eta_{ij} = d\log(z_i - z_j)$.  On overlaps $U_\sigma \cap U_\tau$, the transition data is encoded by the change-of-coordinate forms, which are $\bar{\partial}$-exact on the holomorphic curve $X$.

The cobar complex $\Omega^{\mathrm{ch}}(\mathcal{C})$ computes global sections of $\mathcal{F}_{\mathcal{C}}$ via integration of local cobar elements against logarithmic forms on $\overline{C}_n(X)$.  This is precisely the Čech-de Rham double complex: the Čech direction glues local cobar data across charts, while the de Rham direction is the cobar differential.

\emph{Step 3: Quasi-isomorphism.}
Since $X$ is a smooth algebraic curve, the FM compactification $\overline{C}_n(X)$ is a smooth variety with normal crossings boundary (Theorem~\ref{thm:normal-crossings}).  The cover $\mathfrak{U}^{(n)}$ can be chosen to be a Leray cover: each finite intersection $U_{\sigma_1} \cap \cdots \cap U_{\sigma_k}$ is either empty or contractible (being an intersection of coordinate discs in $C_n(X)$).  For a Leray cover of a smooth variety, the Čech-to-derived-functor spectral sequence degenerates at $E_1$, giving:
\[
\check{H}^p(\mathfrak{U}, \mathcal{F}_{\mathcal{C}}) \cong H^p(X^n, \mathcal{F}_{\mathcal{C}}).
\]
The right-hand side is the factorization homology $\int_X \mathcal{F}_{\mathcal{C}}$, which by the Costello--Gwilliam equivalence (cf.\ \cite{CG17}) agrees with the cobar cohomology $H^*(\Omega^{\mathrm{ch}}(\mathcal{C}))$.
\end{proof}

\subsection{Integration kernels and cobar operations}

\begin{definition}[Cobar integration kernel]\label{def:cobar-kernel}
Elements of the cobar complex can be represented by integration kernels:
\[
K_{p+1}(z_0, \ldots, z_p; w_0, \ldots, w_p) \in \Gamma\left(C_{p+1}(X) \times C_{p+1}(X), \text{Hom}(\mathcal{C}^{\otimes(p+1)}, \mathbb{C}) \otimes \Omega^*\right)
\]
acting on sections of $\mathcal{C}$ by:
\[
(\Phi_K \cdot c)(z_0, \ldots, z_p) = \int_{C_{p+1}(X)} K_{p+1}(z_0, \ldots, z_p; w_0, \ldots, w_p) \wedge c(w_0) \otimes \cdots \otimes c(w_p)
\]
\end{definition}

\begin{example}[Fundamental cobar element]\label{ex:fundamental-cobar}
For the trivial chiral coalgebra $\mathcal{C} = \omega_X$, the fundamental cobar element is:
\[
K_2(z_1, z_2; w_1, w_2) = \frac{1}{(z_1 - w_1)(z_2 - w_2) - (z_1 - w_2)(z_2 - w_1)}
\]
This kernel reconstructs the chiral multiplication from the coalgebra data.
\end{example}

\begin{theorem}[Cobar as free chiral algebra; \ClaimStatusProvedHere]\label{thm:cobar-free}
As a graded chiral algebra (forgetting the differential), the cobar
construction $\Omega^{\mathrm{ch}}(\mathcal{C})$ is the free chiral
algebra generated by $s^{-1}\bar{\mathcal{C}}$, where
$\bar{\mathcal{C}} = \ker(\epsilon\colon \mathcal{C} \to \omega_X)$.
The differential $d_\Omega$ is the unique derivation extending the
reduced comultiplication
$\bar{\Delta}\colon \bar{\mathcal{C}} \to
\bar{\mathcal{C}} \otimes \bar{\mathcal{C}}$
(this is essential data: $\Omega^{\mathrm{ch}}(\mathcal{C})$ is a
\emph{DG} chiral algebra, not merely a free algebra).
\end{theorem}

\begin{proof}
By construction (Definition~\ref{def:geom-cobar-precise}), the underlying graded chiral algebra of $\Omega^{\mathrm{ch}}(\mathcal{C})$ is $\mathrm{Free}_{\mathrm{ch}}(s^{-1}\bar{\mathcal{C}})$, the free chiral algebra generated by $s^{-1}\bar{\mathcal{C}}$ as a $\mathcal{D}_X$-module.  The universal property of free algebras then gives: for any chiral algebra~$\mathcal{A}$ and graded $\mathcal{D}_X$-module morphism $f\colon s^{-1}\bar{\mathcal{C}} \to \mathcal{A}$, there exists a unique chiral algebra morphism $\tilde{f}\colon \mathrm{Free}_{\mathrm{ch}}(s^{-1}\bar{\mathcal{C}}) \to \mathcal{A}$ extending~$f$.

It remains to verify that $d_\Omega$ is a derivation.  Since $\mathrm{Free}_{\mathrm{ch}}$ is left adjoint to the forgetful functor, a derivation on a free algebra is determined by its restriction to generators.  The restriction $d_\Omega|_{s^{-1}\bar{\mathcal{C}}}$ equals the desuspended reduced comultiplication $s^{-1}\bar{\Delta}\colon s^{-1}\bar{\mathcal{C}} \to (s^{-1}\bar{\mathcal{C}})^{\otimes 2} \hookrightarrow \mathrm{Free}_{\mathrm{ch}}(s^{-1}\bar{\mathcal{C}})$, which is a well-defined map of $\mathcal{D}_X$-modules.  The Leibniz extension to all of $\Omega^{\mathrm{ch}}(\mathcal{C})$ is unique, giving $d_\Omega$ as the unique derivation extending $\bar{\Delta}$.
\end{proof}

\subsection{Geometric bar-cobar composition}

\begin{theorem}[Geometric unit of adjunction; \ClaimStatusProvedHere]\label{thm:geom-unit}
\label{thm:bar-cobar-adjunction}
\index{bar-cobar adjunction|textbf}
The unit of the bar-cobar adjunction $\eta: \mathcal{A} \to \Omega^{\text{ch}}(\bar{B}^{\text{ch}}(\mathcal{A}))$ is geometrically realized by:
\[
\eta(\phi)(z) = \sum_{n \geq 0} \int_{\overline{C}_{n+1}(X)} \phi(z) \wedge \text{ev}^*_{0}\left(\bar{B}_n^{\text{ch}}(\mathcal{A})\right) \wedge \omega_n
\]
where:
\begin{itemize}
\item $\text{ev}_0: \overline{C}_{n+1}(X) \to X$ evaluates at the 0-th point
\item $\omega_n$ is the Poincaré dual of the small diagonal
\item The sum converges due to nilpotency/completeness conditions
\end{itemize}
\end{theorem}

\begin{proof}[Geometric proof]
The unit $\eta_{\mathcal{A}} \colon \mathcal{A} \to \Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A}))$ is constructed as follows.  The tautological inclusion $\mathcal{A} \hookrightarrow T^a(s \cdot \bar{\mathcal{A}})$ into the degree-1 component of the tensor algebra, composed with the canonical projection from the tensor algebra to the cobar construction, gives a map of graded $\mathcal{D}_X$-modules.  At higher tensor degrees, the formula in the theorem statement extends this inclusion via configuration space integrals over the Fulton--MacPherson compactifications $\overline{C}_{n+1}(X)$.

\begin{center}
\begin{tikzcd}[row sep=large, column sep=large]
\mathcal{A} \arrow[r, "\text{bar}"] \arrow[dr, "\eta"', bend right=20] &
\bar{B}^{\text{ch}}(\mathcal{A}) \arrow[d, "\text{cobar}"] \\
& \Omega^{\text{ch}}(\bar{B}^{\text{ch}}(\mathcal{A}))
\end{tikzcd}
\end{center}

That $\eta_{\mathcal{A}}$ is a quasi-isomorphism follows from the spectral sequence associated to the bar filtration $F^p = \bigoplus_{n \geq p} \bar{B}^n$.  At the $E_1$ page, the unit reduces to the classical Koszul resolution of $\mathcal{A}$ by $\Omega(\bar{B}(\mathcal{A}))$, which is acyclic by the Koszul hypothesis (Remark~\ref{rem:koszul-chiral}).  The spectral sequence converges to $H^*(\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A})))$ by the completeness of the filtration (Theorem~\ref{thm:completion-necessity}), so $E_1$-acyclicity implies $\eta_{\mathcal{A}}$ is a quasi-isomorphism.

At the geometric level, the key identity underpinning the spectral sequence collapse is:
\[
\int_{\partial \overline{C}_n} \text{Res}_{D_{ij}}[\cdots] = \int_{\overline{C}_n} d[\cdots] = \int_{C_n} \delta_{D_{ij}} \wedge [\cdots]
\]
which shows that residue extraction (bar) and distributional integration (cobar) are inverse operations up to exact terms, so their composition is homotopic to the identity.
\end{proof}

\section{Precise distribution spaces}

\begin{definition}[Distribution space]
The space $\text{Dist}(C_n(X), \mathcal{C}^{\boxtimes n})$ consists of distributional sections with:
\begin{itemize}
\item Prescribed singularities along diagonals
\item Growth conditions at infinity
\item Appropriate transformation under $\mathfrak{S}_n$
\end{itemize}
\end{definition}

\begin{theorem}[Topology; \ClaimStatusProvedHere]\label{thm:weak-topology}
The distribution space $\operatorname{Dist}(C_n(X), \mathcal{C}^{\boxtimes n})$ is a complete locally convex topological vector space under the weak-$*$ topology defined by the pairing:
\[\langle K, \phi \rangle = \int_{C_n(X)} K \cdot \phi\]
for test functions $\phi \in C_c^\infty(C_n(X))$.  The cobar differential $d_\Omega$ is continuous in this topology.
\end{theorem}

\begin{proof}
\emph{Step 1: Topological structure.}
The test function space $C_c^\infty(C_n(X), (\mathcal{C}^{\boxtimes n})^*)$ carries the standard inductive limit topology (over compacta).  The distribution space $\operatorname{Dist}(C_n(X), \mathcal{C}^{\boxtimes n})$ is its continuous dual, equipped with the weak-$*$ topology: a net $K_\alpha \to K$ iff $\langle K_\alpha, \phi \rangle \to \langle K, \phi \rangle$ for all test functions $\phi$.  By the Banach-Alaoglu theorem, bounded subsets of the distribution space are weak-$*$ precompact.  Completeness follows from the completeness of $\mathbb{C}$ and the fact that $C_c^\infty$ is a nuclear LF-space (a strict inductive limit of nuclear Fréchet spaces $C^\infty_K$ indexed by compact exhaustions $K$), so its dual is complete in the weak-$*$ topology by Grothendieck's completeness theorem.

\emph{Step 2: Prescribed singularities.}
The distributions $K \in \operatorname{Dist}(C_n(X), \mathcal{C}^{\boxtimes n})$ have singularities supported on the diagonals $\Delta_{ij} = \{z_i = z_j\}$, of the form $K \sim c_{ij}^{(k)}/(z_i - z_j)^k$ for finitely many $k$ (determined by the OPE orders of $\mathcal{C}$).  This regularity condition defines a closed subspace of the full distribution space, hence inherits completeness.

\emph{Step 3: Continuity of $d_\Omega$.}
The cobar differential $d_\Omega(K) = \sum_{i < j} \delta_{\Delta_{ij}} * K_{\text{coproduct}}$ involves convolution with delta functions supported on diagonals.  For each test function $\phi$, $\langle d_\Omega(K), \phi \rangle = \langle K, d_\Omega^*(\phi) \rangle$ where $d_\Omega^*$ is the formal adjoint (restriction to diagonals followed by the coalgebra coproduct).  Since $d_\Omega^*$ maps $C_c^\infty \to C_c^\infty$ continuously (restriction to a submanifold is continuous in the $C^\infty$ topology), $d_\Omega$ is weak-$*$ continuous.
\end{proof}

\begin{remark}[Regularization methods]\label{rem:regularization-methods}
When distributional products arising in the cobar differential require regularization, three standard methods are available:
\begin{enumerate}
\item \emph{Dimensional regularization}: analytic continuation in dimension $d = d_0 - \epsilon$;
\item \emph{Principal value prescription}: $\mathrm{P.V.}\int f(z)/z\,dz$;
\item \emph{Hadamard finite parts}: extracting the finite part of a divergent integral.
\end{enumerate}
For the cobar construction in the chiral setting, no regularization is needed at genus~$0$ because the distributional products are convolutions with delta functions supported on smooth submanifolds (the diagonals $\Delta_{ij} \subset C_n(X)$), and such convolutions are well-defined by the calculus of wavefront sets~\cite{Hormander}: the conormal bundles $N^*\Delta_{ij}$ do not intersect the wavefront set of the coalgebra coproduct, which is supported along the diagonals themselves.
At higher genus, the propagator acquires distributional corrections requiring the regularization methods listed above; see the genus-$g$ analysis in Theorem~\ref{thm:higher-genus-inversion}.
\end{remark}

\begin{example}[Cobar via integration kernels]\label{ex:cobar-kernels}
The cobar construction uses distributional integration kernels. For a chiral coalgebra $\mathcal{C}$ 
with coproduct $\Delta: \mathcal{C} \to \mathcal{C} \boxtimes \mathcal{C}$, elements of $\Omega^{\text{ch}}(\mathcal{C})$ are:

\[\sum_{n \geq 0} \int_{C_n(X)} K_n(z_1, \ldots, z_n) \cdot c_1(z_1) \cdots c_n(z_n) \, dz_1 \cdots dz_n\]

where:
\begin{itemize}
\item $K_n$ are distributions on $C_n(X)$ (typically with poles on diagonals)
\item $c_i \in \mathcal{C}$ are coalgebra elements  
\item Integration is regularized via analytic continuation or principal values
\end{itemize}

The cobar differential acts by:
\[d_{\text{cobar}} = \sum_{i<j} \Delta_{ij} \cdot \delta(z_i - z_j)\]
inserting Dirac distributions that ``pull apart'' colliding points.

This realizes the cobar complex as the Koszul dual to the bar complex under the pairing:
\[\langle \omega_{\text{bar}}, K_{\text{cobar}} \rangle = \int_{\overline{C}_n(X)} \omega_{\text{bar}} \wedge \iota^* K_{\text{cobar}}\]
where $\iota: C_n(X) \hookrightarrow \overline{C}_n(X)$ is the inclusion.

\emph{Physical interpretation.} In quantum field theory:
\begin{itemize}
\item Bar elements = algebraic shadow data for off-shell states with infrared cutoffs
\item Cobar elements = algebraic shadow data for on-shell propagators with UV regularization
\item The pairing = conjectural algebraic shadow of S-matrix elements
\end{itemize}
\end{example}

\subsection{Poincaré--Verdier duality realization}

\begin{theorem}[Bar-cobar as Poincaré--Verdier duality; \ClaimStatusProvedHere]\label{thm:poincare-verdier}
The bar and cobar constructions are related by Poincaré--Verdier duality:
\[
\bar{B}^{\text{ch}}(\mathcal{A}) \cong \mathbb{D}(\Omega^{\text{ch}}(\mathcal{A}^!))
\]
where $\mathbb{D}$ denotes Verdier duality and $\mathcal{A}^!$ is the Koszul dual.
\end{theorem}

\begin{proof}[Geometric realization]
The duality is realized through the perfect pairing:
\[
\langle \omega_{\text{bar}}, \omega_{\text{cobar}} \rangle = \int_{\overline{C}_n(X)} \omega_{\text{bar}} \wedge \iota^*\omega_{\text{cobar}}
\]
where $\iota: C_n(X) \hookrightarrow \overline{C}_n(X)$ is the inclusion.

The duality has the following structure:
\begin{itemize}
\item Logarithmic forms on $\overline{C}_n(X)$ (bar) are dual to distributions on $C_n(X)$ (cobar)
\item Residues at divisors (bar) are dual to principal value integrals (cobar)
\item Collision divisors (bar) correspond to extension loci (cobar)
\item The duality exchanges extraction (analysis) with reconstruction (synthesis)
\end{itemize}
\end{proof}

\subsection{Explicit cobar computations}

\begin{example}[Cobar of exterior coalgebra]\label{ex:cobar-exterior}
Let $\mathcal{E} = \Lambda^*_{\text{ch}}(V)$ be the chiral exterior coalgebra on generators $V$. Then:
\[
\Omega^{\text{ch}}(\mathcal{E}) \cong S_{\text{ch}}(s^{-1}V)
\]
the chiral symmetric algebra on the desuspension of $V$. 

Geometrically, this duality is realized by:
\begin{itemize}
\item Fermionic fields $\psi \in V$ with antisymmetric OPE become bosonic fields $\phi \in s^{-1}V$ with symmetric OPE
\item The cobar differential vanishes since the reduced comultiplication $\bar{\Delta}(\psi) = 0$
\item Configuration space integrals enforce bosonic statistics through symmetric integration domains
\end{itemize}

This is the chiral analogue of the classical Koszul duality between exterior and symmetric algebras.
\end{example}

\begin{example}[Cobar of bar of free fermions]\label{ex:cobar-bar-fermion}
For the free fermion algebra $\mathcal{F}$, bar-cobar inversion gives:
\[
\Omega^{\text{ch}}(\bar{B}^{\text{ch}}(\mathcal{F})) \xrightarrow{\sim} \mathcal{F}
\]
recovering the free fermion algebra itself (not the $\beta\gamma$ system).  The Koszul dual $\mathcal{F}^! \cong \beta\gamma$ is obtained instead by linear duality of the bar coalgebra: $\mathcal{F}^! = \bar{B}^{\text{ch}}(\mathcal{F})^\vee$ (see Example~\ref{ex:fermion-betagamma-bar-cobar} and Theorem~\ref{thm:fermion-boson-koszul}).  This distinction is the chiral analog of the classical fact that $\Omega(\bar{B}({\Lambda}(V))) \simeq {\Lambda}(V)$ (bar-cobar inversion), while ${\Lambda}(V)^! = \mathrm{Sym}(V^*)$ (Koszul dual algebra via linear duality).
\end{example}


\subsection{\texorpdfstring{Cobar $A_\infty$ structure}{Cobar A-infinity structure}}

\begin{theorem}[\texorpdfstring{$A_\infty$}{A-infinity} structure on cobar {\cite{LV12}}; \ClaimStatusProvedElsewhere]\label{thm:cobar-ainfty}
The cobar construction $\Omega^{\text{ch}}(\mathcal{C})$ carries a canonical $A_\infty$ structure with operations:
\[
m_k: \Omega^{\text{ch}}(\mathcal{C})^{\otimes k} \to \Omega^{\text{ch}}(\mathcal{C})[2-k]
\]
geometrically realized by:
\[
m_k(\alpha_1, \ldots, \alpha_k) = \int_{\partial \overline{M}_{0,k+1}} \alpha_1 \wedge \cdots \wedge \alpha_k \wedge \omega_{0,k+1}
\]
where $\overline{M}_{0,k+1}$ is the moduli space of stable curves with $k+1$ marked points.
\end{theorem}

\begin{proof}
By \cite[Theorem~9.2.8]{LV12}, $A_\infty$ structures arise from operadic bar-cobar resolutions.
The boundary stratification of the Deligne--Mumford compactification gives:
\[
\partial \overline{M}_{0,k+1} = \bigcup_{\substack{I \sqcup J = [k+1] \\ |I|,|J| \geq 2}} \overline{M}_{0,|I|+1} \times \overline{M}_{0,|J|+1}
\]
Each boundary stratum $\overline{M}_{0,|I|+1} \times \overline{M}_{0,|J|+1}$ contributes a composition $m_{|I|} \circ m_{|J|}$ to the boundary of $m_k$. The topological identity $\partial^2 = 0$ on the chain complex $C_*(\overline{M}_{0,k+1})$ then gives $\sum_{i+j=k+1} m_i \circ m_j = 0$, which is the $A_\infty$ relation. Signs are determined by the orientation of the boundary strata, matching the Koszul sign convention in \cite[\S10.3]{LV12}.
\end{proof}

\subsection{Geometric cobar for curved coalgebras}

\begin{definition}[Curved cobar]\label{def:curved-cobar}
For a curved chiral coalgebra $(\mathcal{C}, \kappa_C)$ with curvature element $\kappa_C \in \mathcal{C}^{\otimes 2}[2]$, the cobar complex has modified differential:
\[
d_{\text{curved}} = d_{\text{cobar}} + m_0
\]
where $m_0 \in \Omega^{\text{ch}}(\mathcal{C})[2]$ is the curvature term geometrically realized by:
\[
m_0 = \int_{S^1 \times X} \kappa_C(z, w) \wedge K_{\text{prop}}(z, w)
\]
with $K_{\text{prop}}$ the propagator kernel encoding quantum corrections.
\end{definition}

\begin{theorem}[Curved Maurer--Cartan equation; \ClaimStatusProvedHere]\label{thm:curved-mc-cobar}
\textup{[Regime: curved-central
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

Elements $\alpha \in \Omega^{\text{ch}}(\mathcal{C})[-1]$ satisfying the curved Maurer--Cartan equation:
\[
d_{\text{curved}}\alpha + \frac{1}{2}m_2(\alpha, \alpha) + m_0 = 0
\]
correspond geometrically to:
\begin{itemize}
\item Deformations of the chiral structure that do not preserve the grading
\item Quantum anomalies in the conformal field theory
\item Central extensions and their geometric representatives
\end{itemize}
\end{theorem}

\begin{proof}
By the general theory of curved $A_\infty$ algebras (Positselski~\cite{Positselski11}, Loday--Vallette~\cite{LV12} \S10.1), the curved Maurer--Cartan equation $d\alpha + \frac{1}{2}[\alpha,\alpha] + m_0 = 0$ parametrizes gauge equivalence classes of curved deformations.  In the chiral setting, $m_0 \in \Omega^{\mathrm{ch}}(\mathcal{C})$ is the curvature element.  The three geometric correspondences are:
(i) A solution $\alpha$ defines a twisted differential $d_\alpha = d + [\alpha, -]$ satisfying $d_\alpha^2 = 0$, which deforms the chiral structure.
(ii) The curvature $m_0$ is the genus-0 obstruction to $d^2 = 0$; for a chiral algebra with central charge $c$, $m_0 \propto c$ (Proposition~\ref{prop:km-bar-curvature}), which is the conformal anomaly.
(iii) At genus 1, solutions $\alpha$ with $m_0 = 0$ classify central extensions of the chiral algebra by $\mathbb{C}$, as established in Section~\ref{sec:genus_1_central_extensions}.
\end{proof}

\begin{proposition}[Curvature of the affine bar complex; \ClaimStatusProvedHere]
\label{prop:km-bar-curvature}
\index{curvature!affine bar complex}
For the affine Kac--Moody chiral algebra $\widehat{\mathfrak{g}}_k$ at level $k$, the bar complex $\bar{B}^{\mathrm{ch}}(\widehat{\mathfrak{g}}_k)$ has curvature
\begin{equation}\label{eq:km-curvature-part1}
m_0 = \frac{k + h^\vee}{2h^\vee} \cdot \kappa
\end{equation}
where $h^\vee$ is the dual Coxeter number and $\kappa = \sum_a J^a \otimes J_a$ is the Casimir element (not to be confused with the abstract curvature $\kappa_C$ of Definition~\ref{def:curved-cobar}).  In particular:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $m_1^2 = 0$ \textup{(}i.e., $d^2 = 0$ on the internal differential\textup{)} if and only if $k = -h^\vee$ \textup{(}critical level\textup{)};
\item The total bar differential $d_B$ always satisfies $d_B^2 = 0$, regardless of the level.
\end{enumerate}
\end{proposition}

\begin{proof}
The bar differential on degree-$1$ elements $J^a \boxtimes J^b \cdot \eta_{12}$ extracts the OPE:
\[
d(J^a \boxtimes J^b \cdot \eta_{12}) = k \cdot (J^a, J^b) \cdot |0\rangle + f^{ab}{}_{c}\, J^c,
\]
where the first term comes from the double-pole $k(J^a,J^b)/(z-w)^2$.
Applying $m_1$ twice and using the Jacobi identity gives
\[
m_1^2(J^a \boxtimes J^b \cdot \eta_{12}) = (k + h^\vee) \cdot (\text{adjoint Casimir}),
\]
since the Killing form contraction $\sum_{c,d} f^{ac}{}_d f^{bc}{}_d = 2h^\vee \cdot \delta^{ab}$ (with long roots normalized to length $2$).  The factor $h^\vee$ is the eigenvalue of the adjoint Casimir; the total coefficient $k + h^\vee$ vanishes precisely at critical level.

For $\mathfrak{g} = \mathfrak{sl}_2$ with $h^\vee = 2$, the explicit computation:
$m_1(e \boxtimes f \cdot \eta_{12}) = k \cdot \mathbf{1} + h$ (from
$e_{(0)}f = h$ and $e_{(1)}f = k$).  Applying $m_1$ again:
$m_1(h) = 0$ (since $h$ is primitive) and
$m_1(\mathbf{1}) = 0$, but the composite $m_1^2$ on degree-$2$
elements picks up the adjoint action:
$m_1^2(e \boxtimes f \cdot \eta_{12}) = [h, k \cdot \mathbf{1} + h]_{\mathrm{bar}}
= k \cdot (\text{ad-action of Casimir}) + 2h = (k+2) \cdot \partial h$.
\end{proof}

\begin{remark}[Feigin--Frenkel center at critical level]
\label{rem:feigin-frenkel-center}
\index{Feigin--Frenkel center}
At the critical level $k = -h^\vee$, Proposition~\ref{prop:km-bar-curvature}(i) gives $m_1^2 = 0$, so the bar complex is \emph{uncurved}.  A foundational result of Feigin--Frenkel~\cite{Feigin-Frenkel} shows that the center of $\widehat{\mathfrak{g}}_{-h^\vee}$ is then isomorphic to the algebra of functions on $\mathfrak{g}^\vee$-opers:
\[
Z(\widehat{\mathfrak{g}}_{-h^\vee}) \cong \mathrm{Fun}(\mathrm{Op}_{\check{\mathfrak{g}}}(X)).
\]
The critical level is the fixed point of the level-shifting involution $k \mapsto -k - 2h^\vee$, and the uncurved bar complex recovers $\widehat{\mathfrak{g}}_{-h^\vee}$ via cobar.  See Part~II for the detailed treatment.
\end{remark}

\begin{corollary}[Level-shifting duality; \ClaimStatusProvedHere]
\label{cor:level-shifting-part1}
\index{Feigin--Frenkel duality}
\index{level!shifted}
For any simple Lie algebra $\mathfrak{g}$ and level $k \neq -h^\vee$, the bar-cobar adjunction applied to the curved bar complex of Proposition~\ref{prop:km-bar-curvature} gives
\begin{equation}\label{eq:level-shifting-part1}
\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\widehat{\mathfrak{g}}_k)) \;\simeq\; \widehat{\mathfrak{g}}_{-k-2h^\vee}.
\end{equation}
When $k \neq -h^\vee$ the bar complex is curved, so Theorem~\ref{thm:bar-cobar-isomorphism-main} (which requires the Koszul/uncurved hypothesis) does not apply directly; the level-shifting formula holds at the level of the curved bar-cobar adjunction before passing to cohomology.

The dual level $k' = -k - 2h^\vee$ satisfies:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $k + k' = -2h^\vee$;
\item the central charges satisfy $c(\widehat{\mathfrak{g}}_k) + c(\widehat{\mathfrak{g}}_{k'}) = 2\dim\mathfrak{g}$ \textup{(}Theorem~\ref{thm:central-charge-complementarity}\textup{)};
\item the curvatures are opposite: $m_0(k') = -m_0(k)$.
\end{enumerate}
\end{corollary}

\begin{proof}
The bar-cobar adjunction (Theorem~\ref{thm:bar-cobar-adjunction}, which applies to curved coalgebras without the Koszul hypothesis) applied to the curved coalgebra $\bar{B}^{\mathrm{ch}}(\widehat{\mathfrak{g}}_k)$ recovers a chiral algebra whose OPE is determined by the bar data via the Verdier pairing (Theorem~\ref{thm:verdier-bar-cobar}).  The desuspension $s^{-1}$ in the cobar construction introduces a sign reversal in the curvature: the cobar algebra $\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\widehat{\mathfrak{g}}_k))$ has curvature $m_0' = -m_0$.  Combining with the curvature formula $m_0 = (k+h^\vee)\kappa/(2h^\vee)$ (Proposition~\ref{prop:km-bar-curvature}), the cobar curvature is
\[
m_0' = -\frac{k + h^\vee}{2h^\vee}\,\kappa = \frac{k' + h^\vee}{2h^\vee}\,\kappa
\quad\text{where } k' = -k - 2h^\vee.
\]
Since the simple-pole data $f^{ab}{}_c$ (the Lie bracket) is unchanged by the bar-cobar passage and the double-pole coefficient is determined by the curvature, the cobar algebra has OPE
\[
J^{\prime a}(z) J^{\prime b}(w) \sim \frac{k'\,(J^a, J^b)}{(z-w)^2} + \frac{f^{ab}{}_c\, J^{\prime c}(w)}{z-w}
\]
with $k' = -k - 2h^\vee$.  Parts~(i)--(iii) follow by direct substitution.
\end{proof}

\subsection{Computational algorithms for cobar}

\begin{remark}[Cobar complex computation]
Given a chiral coalgebra $\mathcal{C}$ with basis $\{e_i\}$, structure constants $\Delta(e_i) = \sum_{j,k} c_{jk}^i e_j \otimes e_k$, and counit $\epsilon$, the cobar complex $(\Omega^{\mathrm{ch}}(\mathcal{C}), d_{\mathrm{cobar}})$ is constructed as follows.
\begin{enumerate}
\item Initialize $\Omega^0 = \mathrm{Free}_{\mathrm{ch}}(s^{-1}\bar{\mathcal{C}})$ where $\bar{\mathcal{C}} = \ker(\epsilon)$.
\item For each generator $s^{-1}e_i$ with $\epsilon(e_i) = 0$, compute $d(s^{-1}e_i) = -\sum_{j,k} c_{jk}^i \, s^{-1}e_j \otimes s^{-1}e_k$.
\item Extend to products by the Leibniz rule: $d(xy) = d(x)y + (-1)^{|x|}xd(y)$.
\item For each $n$-fold product, tensor with $\Omega^*(C_{n+1}(X))$.
\item Impose Arnold--Orlik--Solomon relations among logarithmic forms and factorization constraints from the chiral structure.
\end{enumerate}
\end{remark}

\section{Genus 1 contributions: central extensions in the bar-cobar complex}
\label{sec:genus_1_central_extensions}

Everything constructed so far lives on a \emph{fixed} curve~$X$.
The bar differential is a residue on $\overline{C}_n(X)$; the
cobar differential inserts delta functions on $C_n(X)$; Verdier
duality exchanges the two.  None of this involves the moduli of
curves.

Now let the curve vary.  Replace $X$ by a family
$\pi \colon \mathcal{X} \to S$ over a base~$S$, and ask: how does
the bar complex change as $X$ moves in $\overline{\mathcal{M}}_g$?
At genus~$0$ the answer is: it does not --- there are no moduli.
At genus~$1$, the propagator $K^{(1)} = \theta_1'/\theta_1$
depends on the modular parameter $\tau$, and the bar differential
acquires a correction.  This correction is the central extension:
curvature $m_0 = \kappa(\cA)$ emerges because the trace of the
OPE around the $A$-cycle of the torus is nonzero.  The central
charge, invisible at genus~$0$, is the first shadow of the
universal Maurer--Cartan class $\Theta_{\cA}$.

\subsection{Central extensions at genus 1: intuition}

\subsubsection{Physical picture}

Consider the Heisenberg vertex algebra with generators $a(z), a^*(z)$ satisfying:
\[[a(z), a^*(w)] \sim \frac{\kappa}{(z-w)^2}\]
where $\kappa$ is the central charge.

\begin{center}
\begin{tikzcd}[column sep=large]
\text{Genus 0} \arrow[r, "\text{OPE}"] & 
\frac{1}{(z-w)^2} \arrow[d, "\text{residue}"] \\
& 0 \arrow[d, "\text{explanation}"'] \\
& \text{Tree-level: no cycles}
\end{tikzcd}
\quad\quad
\begin{tikzcd}[column sep=large]
\text{Genus 1} \arrow[r, "\operatorname{Tr}"] & 
\oint \frac{\kappa \, dz}{z^2} \arrow[d, "\text{residue}"] \\
& \kappa \arrow[d, "\text{explanation}"'] \\
& \text{One-loop: central charge}
\end{tikzcd}
\end{center}

The double pole $1/(z-w)^2$ in the OPE produces different behavior at each genus: at genus~0, residues at $z=w$ give derivatives of delta functions that integrate to zero over the sphere; at genus~1, the \emph{trace} $\operatorname{Tr}(a \otimes a^*)$ around the $S^1$ cycle picks up the $\kappa$ coefficient as a non-vanishing residue.

This is the first manifestation of the principle that central extensions are intrinsically one-loop phenomena.

\subsubsection{Absence at genus 0}

Consider the genus 0 bar differential on $\mathcal{A} \otimes \mathcal{A}$:
\[d^{(0)}(a \otimes b) = \mu(a \otimes b) - a \otimes \mathbbm{1} - \mathbbm{1} \otimes b\]
where $\mu$ is the OPE product.

For central terms: $\mu(a \otimes a^*) \sim \kappa \cdot \mathbbm{1}$

But $d^{(0)}(\kappa \cdot \mathbbm{1}) = \kappa \cdot \mathbbm{1} - \kappa \cdot \mathbbm{1} - \kappa \cdot \mathbbm{1} = -\kappa \cdot \mathbbm{1}$

So the cocycle $a \otimes a^* - \kappa \cdot \mathbbm{1}$ satisfying $d^{(0)}(\cdots) = 0$
would require $\kappa = 0$. The central charge cannot appear at genus 0.

\subsection{The geometric construction: configuration spaces on the torus}

\subsubsection{Setup: the genus 1 configuration space}

Let $\mathbb{T}^2 = \mathbb{C}/\Lambda$ be a torus with period lattice $\Lambda$.
Define:
\[\mathrm{Conf}_n(\mathbb{T}^2) = \{ (z_1, \ldots, z_n) \in (\mathbb{T}^2)^n \mid z_i \neq z_j \}\]

The genus 1 bar complex is:
\[C_{\bullet}^{(1)}(\mathcal{A}) = \mathcal{C}_{\bullet}(\mathrm{Conf}_{\bullet}(\mathbb{T}^2), 
\mathcal{A}^{\boxtimes \bullet})\]
chains on configuration space with coefficients in $\mathcal{A}$.

\subsubsection{The trace element}

The key new element at genus 1 is the \emph{trace operation}. For $a \in \mathcal{A}$,
define:
\[\operatorname{Tr}(a) = \int_{S^1 \subset \mathbb{T}^2} \mathrm{ev}^*(a) \in C_0^{(1)}(\mathcal{A})\]
where $\mathrm{ev}: \mathbb{T}^2 \to X$ is the constant map to the base curve.

More explicitly, using the uniformization $\mathbb{T}^2 = \mathbb{C}/\mathbb{Z} \oplus \tau \mathbb{Z}$:
\[\operatorname{Tr}(a) = \oint_{|z| = 1} \rho_{\mathbb{T}^2}(a(z)) \frac{dz}{2\pi i z}\]
where $\rho_{\mathbb{T}^2}$ is the regularized insertion on the torus.

\subsubsection{Explicit formula for central charge cocycle}

For the Heisenberg algebra, consider:
\[c_1 = \operatorname{Tr}(a \otimes a^*) - \kappa \cdot \mathbbm{1} 
\in C_1^{(1)}(\mathcal{A}) \otimes C_1^{(1)}(\mathcal{A})\]

\begin{theorem}[Central charge cocycle; \ClaimStatusProvedHere]\label{thm:central-charge-cocycle}
\textup{[Regime: curved-central
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

The element $c_1$ satisfies:
\[d^{(1)} c_1 = 0\]
and represents the central extension in $H_1^{(1)}(\mathcal{A})$.

Moreover, the class $[c_1]$ is:
\begin{itemize}
\item Non-trivial: $[c_1] \neq 0$ in homology
\item Universal: independent of the choice of cycle on $\mathbb{T}^2$
\item Generates: all genus 1 central phenomena factor through $[c_1]$
\end{itemize}
\end{theorem}

\begin{proof}
The differential $d^{(1)}$ at genus 1 includes:
\begin{enumerate}
\item Standard bar differential (as at genus 0)
\item \emph{New term:} Contraction around the $S^1$ cycle
\end{enumerate}

Computing:
\begin{align}
d^{(1)}[\operatorname{Tr}(a \otimes a^*)] 
&= \operatorname{Tr}[\mu(a \otimes a^*)] - \operatorname{Tr}(a) \otimes \operatorname{Tr}(a^*) \\
&= \operatorname{Tr}[\kappa \cdot \mathbbm{1}] - 0 \quad \text{($\operatorname{Tr}(a) = \operatorname{Tr}(a^*) = 0$ for non-vacuum modes)} \\
&= \kappa \cdot \mathbbm{1} \quad \text{(normalized trace: $\operatorname{Tr}(\mathbbm{1}) = 1$)}
\end{align}

Therefore: $d^{(1)}[\operatorname{Tr}(a \otimes a^*) - \kappa \cdot \mathbbm{1}] = 0$.
\end{proof}

\subsection{Formal calculations: degree-by-degree analysis}

\subsubsection{Degree 0: the vacuum}

$C_0^{(1)} = \mathbb{C} \cdot \mathbbm{1}$, the vacuum state.

\subsubsection{Degree 1: trace insertions}

\[C_1^{(1)} = \operatorname{span}\{ \operatorname{Tr}(a_n), \operatorname{Tr}(a^*_n) \mid n \in \mathbb{Z} \}\]

The differential $d^{(1)}: C_1^{(1)} \to C_0^{(1)}$ maps:
\begin{align}
d^{(1)}[\operatorname{Tr}(a_n)] &= 0 \quad \text{for } n \neq 0 \\
d^{(1)}[\operatorname{Tr}(a_0)] &= 0 \quad \text{(but $a_0 = 0$ in Heisenberg)}
\end{align}

\emph{Homology.} $H_1^{(1)} = \operatorname{span}\{ [\operatorname{Tr}(a_n)], [\operatorname{Tr}(a^*_n)] \mid n \neq 0 \}$

\subsubsection{Degree 2: the central charge emerges}

\[C_2^{(1)} = \operatorname{span}\{ 
\operatorname{Tr}(a_m \otimes a^*_n), 
\operatorname{Tr}(a_m \otimes a_n), 
\operatorname{Tr}(a^*_m \otimes a^*_n) 
\}\]

\emph{The computation.}
\begin{align}
d^{(1)}[\operatorname{Tr}(a_m \otimes a^*_n)] 
&= \operatorname{Tr}[\text{OPE}(a_m, a^*_n)] \\
&= \operatorname{Tr}\left[ \sum_{k \geq 0} \binom{m}{k} a^*_{m+n+k} \cdot a_{-k} 
+ \kappa m \delta_{m+n,0} \cdot \mathbbm{1} \right] \\
&= \kappa m \delta_{m+n,0} \cdot \mathbbm{1}
\end{align}

Here we used $\operatorname{Tr}(a^*_i \cdot a_j) = 0$ always (no tadpoles).

The central charge $\kappa$ appears only in the $m+n=0$ term, corresponding to modes that go around the $S^1$ cycle exactly once: geometrically, $\kappa$ measures the obstruction to extending the Heisenberg algebra to the loop algebra.

\subsubsection{Degrees 3--5: modular corrections}

At degree 3, we have triple traces:
\[\operatorname{Tr}(a_{m_1} \otimes a_{m_2} \otimes a^*_n)\]

The differential now includes pairwise OPE contractions (three terms) and tadpole corrections from $\kappa$ (when indices sum to zero).

\emph{Degree 3 cocycle example:}
\[c_3 = \operatorname{Tr}(a_1 \otimes a_1 \otimes a^*_{-2}) 
- \kappa \cdot \operatorname{Tr}(a_1) + \text{(boundary terms)}\]

At degrees 4 and 5, we see:
\begin{itemize}
\item Multiple $\kappa$ insertions
\item Modular dependence on the torus parameter $\tau$
\item Connection to Eisenstein series $E_2(\tau)$ at weight 2
\end{itemize}

\subsection{The cobar resolution: recovering central extensions}

The cobar construction $\Omega C_{\bullet}^{(1)}(\mathcal{A})$ recovers the
centrally extended algebra $\widehat{\mathcal{A}}$.

\begin{theorem}[Genus 1 cobar-bar duality; \ClaimStatusProvedHere]\label{thm:genus1-cobar-bar}
\textup{[Regime: curved-central, genus-$1$
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

Let $\mathcal{A}$ be a vertex algebra with central charge $\kappa$. Then:
\[H^0(\Omega C_{\bullet}^{(1)}(\mathcal{A})) \cong \widehat{\mathcal{A}}\]
where $\widehat{\mathcal{A}}$ is the universal central extension of $\mathcal{A}$.

The central extension is encoded by the genus 1 cocycle:
\[\omega_{\kappa} = \operatorname{Tr}(a \otimes a^*) - \kappa \cdot \mathbbm{1}\]
\end{theorem}

\begin{proof}
The genus-1 bar complex $C_\bullet^{(1)}(\mathcal{A})$ is built on configuration spaces over the elliptic curve $E_\tau$.  We compute the cobar $\Omega C_\bullet^{(1)}$ and show its zeroth cohomology is the universal central extension.

\emph{Step 1: Genus-1 bar complex in low degrees.}
At degree~0, $C_0^{(1)} = \mathbb{C}$.  At degree~1, $C_1^{(1)} = \Gamma(\overline{C}_2(E_\tau), \mathcal{A} \boxtimes \mathcal{A} \otimes \Omega^1_{\log})$, where the logarithmic form is the elliptic propagator $\eta_{12}^{(1)} = d\log\theta_1(z_{12}|\tau)$.  At degree~2, $C_2^{(1)}$ involves triple products with genus-1 logarithmic 2-forms.

\emph{Step 2: The genus-1 cocycle.}
The bar differential $d: C_1^{(1)} \to C_0^{(1)}$ maps
\[
d(a \otimes b \cdot \eta_{12}^{(1)}) = \mathrm{Res}_{z_1=z_2}[a(z_1)b(z_2) \cdot \eta_{12}^{(1)}] + \int_{E_\tau} a \otimes b \cdot d\eta_{12}^{(1)}.
\]
The first term is the genus-0 collision residue.  The second term is new at genus~1: the propagator $\eta_{12}^{(1)} = d\log\theta_1(z_{12}|\tau)$ is a closed meromorphic 1-form on $E_\tau$ (away from poles), but its $B$-cycle monodromy is non-trivial: $\oint_B \eta_{12}^{(1)} = 2\pi i$.  This monodromy defect, which we write formally as $\int_{E_\tau} \delta_B \eta_{12}^{(1)} = 2\pi i\, \omega_\tau$ (where $\omega_\tau$ is the normalized holomorphic 1-form on $E_\tau$), gives
\[
\int_{E_\tau} a \otimes b \cdot 2\pi i\, \omega_\tau = 2\pi i \cdot \mathrm{Tr}(a \otimes b)
\]
where $\mathrm{Tr}(a \otimes b) = \oint a(z)b(z)\, dz$ is the trace pairing on $\mathcal{A}$.

\emph{Step 3: Cobar complex computation.}
The cobar $\Omega C_\bullet^{(1)}$ has generators dual to $C_1^{(1)}$ and differential encoded by the structure maps of the coalgebra $C_\bullet^{(1)}$.  The zeroth cohomology $H^0(\Omega C_\bullet^{(1)})$ is the algebra generated by the dual generators modulo the relations imposed by~$d_\Omega$.

The genus-1 contribution to $d_\Omega$ produces the central extension relation: for generators $J^a$ of~$\mathcal{A}$,
\[
[J^a, J^b]_{\widehat{\mathcal{A}}} = [J^a, J^b]_{\mathcal{A}} + \kappa \cdot \mathrm{Tr}(J^a \otimes J^b) \cdot \mathbf{K}
\]
where $\mathbf{K}$ is the central element and $\kappa$ is the central charge.  This is precisely the relation defining the universal central extension $\widehat{\mathcal{A}}$.

\emph{Step 4: Universality.}
The resulting central extension is universal because any 2-cocycle $\omega: \mathcal{A} \otimes \mathcal{A} \to \mathbb{C}$ that defines a central extension of~$\mathcal{A}$ factors through the genus-1 trace pairing.  Indeed, the Hochschild 2-cocycle condition requires $\omega$ to be $\mathcal{A}$-bilinear and invariant, which forces $\omega = c \cdot \mathrm{Tr}$ for some constant~$c$.  The genus-1 construction produces exactly this with $c = \kappa$.
\end{proof}

\begin{remark}[Central extension as genus-\texorpdfstring{$1$}{1} component of \texorpdfstring{$\Theta$}{Theta}]
\label{rem:central-ext-theta1}
The central extension cocycle $\omega_\kappa = \kappa \cdot
\mathrm{Tr}$ is exactly the genus-$1$ component $\theta_1$ of
the universal MC class (Theorem~\ref{thm:explicit-theta}):
$\theta_1 = \kappa(\cA) \cdot \mu \otimes \lambda_1$,
where $\mu = [-,-]$ is the Lie bracket and $\lambda_1$ is the
Hodge class.  The universality of the central extension is a
shadow of the universality of $\Theta_{\cA}$: there is only one
direction for genus-$1$ deformations because
$H^2_{\mathrm{cyc}}(\mathfrak{g},\mathfrak{g}) \cong \mathbb{C}$.
\end{remark}

\subsection{Comparison with physical literature}

Our construction recovers known results from physics:

\begin{itemize}
\item \emph{Kac--Moody algebras:} The level $k$ of a Kac--Moody algebra is precisely
the central charge $\kappa$ appearing in our genus 1 cocycle

\item \emph{Virasoro central charge:} For the Virasoro vertex algebra, the central
charge $c$ appears as $\operatorname{Tr}(L_m \otimes L_n)$ with $m+n = 0$

\item \emph{$W$-algebras:} For $W$-algebras (following Arakawa), higher-weight
central charges appear at genus 1 in traces of higher-weight operators
\end{itemize}

\subsection{Genus 1 summary}

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
\emph{Algebra} & \textbf{Physics} & \textbf{Bar-Cobar} \\
\hline
Central extension & One-loop correction & Genus 1 cocycle \\
Central charge $\kappa$ & Quantum parameter & Trace coefficient \\
Level of Kac--Moody & UV divergence & $H_2^{(1)}$ class \\
Virasoro $c$ & Conformal anomaly & $\operatorname{Tr}(T \otimes T)$ \\
\hline
\end{tabular}
\end{center}

\begin{remark}[Functoriality]
The entire construction is functorial: a morphism $\mathcal{A} \to \mathcal{B}$
of vertex algebras preserving central charge induces:
\[C_{\bullet}^{(1)}(\mathcal{A}) \to C_{\bullet}^{(1)}(\mathcal{B})\]
respecting the central extension cocycles. This is the Grothendieck perspective:
genus 1 phenomena are determined by functoriality from genus 0 data plus the
choice of torus.
\end{remark}

\subsection{Extension theory: from genus 0 to higher genus}

\subsubsection{The obstruction complex}

Not every genus 0 chiral algebra extends to higher genus. The obstructions live in specific cohomology groups:

\begin{theorem}[Extension obstruction {\cite{BD04}}; \ClaimStatusProvedElsewhere]
\label{thm:extension-obstruction-bar}
Let $\mathcal{A}$ be a chiral algebra on $\mathbb{CP}^1$. The obstruction to extending $\mathcal{A}$ to genus $g$ lies in:
\[
\text{Obs}_g(\mathcal{A}) \in H^2(\overline{\mathcal{M}}_g, \mathcal{E}nd(\mathcal{A})_0)
\]
where $\mathcal{E}nd(\mathcal{A})_0$ is the sheaf of traceless endomorphisms.
\end{theorem}

\begin{proof}
By the deformation theory of chiral algebras on families of curves (Theorem~\ref{thm:obstruction-quantum}), there is a long exact sequence:
\[
0 \to H^1(\Sigma_g, \mathcal{A}) \to \text{Ext}_{\Sigma_g}(\mathcal{A}) \to H^2(\mathcal{M}_g, \mathbb{C}) \to \text{Obs}_g(\mathcal{A}) \to 0
\]
The obstruction lives in $H^2(\mathcal{M}_g, \mathrm{End}(\mathcal{A})_0)$ with local system coefficients. For specific classes:
\begin{enumerate}
\item For the matter-ghost BRST system, the obstruction vanishes when $c_{\text{matter}} = 26$ (cancellation with $c_{\text{ghost}} = -26$).
\item For a general chiral algebra $\mathcal{A}$, the obstruction depends on $[\omega_g] \in H^2(\mathcal{M}_g, Z(\mathcal{A}))$, where $Z(\mathcal{A})$ is the center.
\item Free theories (Heisenberg at any level, free fermions with spin structure) extend to all genera without central charge restrictions, as the curvature $m_0$ is central and the obstruction class is scalar (Proposition~\ref{prop:km-bar-curvature}).
\end{enumerate}
\end{proof}

\begin{example}[Free fermion extension]
The free fermion extends to all genera with spin structure:

For genus 1: The extension depends on the choice of spin structure (periodic/antiperiodic boundary conditions):
\[
\mathcal{F}_{E_\tau}^{\text{NS}} = \bigoplus_{n \in \mathbb{Z}} \mathcal{F}_n \quad \text{(Neveu--Schwarz)}
\]
\[
\mathcal{F}_{E_\tau}^{\text{R}} = \bigoplus_{n \in \mathbb{Z} + 1/2} \mathcal{F}_n \quad \text{(Ramond)}
\]

The partition function encodes the obstruction:
\[
Z_{\text{ferm}}(\tau) = \frac{\theta_3(0|\tau)}{\eta(\tau)} \quad \text{(NS sector)}
\]
\end{example}

\subsubsection{The tower of extensions}

\begin{theorem}[Universal extension tower; \ClaimStatusProvedHere]\label{thm:universal-extension-tower}
There exists a tower of extensions:
\[
\cA_0 \to \cA_1 \to \cA_2 \to \cdots \to \cA_\infty
\]
where:
\begin{itemize}
\item $\cA_0$: Original genus 0 algebra
\item $\cA_g$: Extension to genus $\leq g$
\item $\cA_\infty$: Universal extension to all genera
\end{itemize}

The connecting maps are given by:
\[
\cA_g \to \cA_{g+1}: \quad a \mapsto a + \sum_{\gamma \in H_1(\Sigma_{g+1})} \oint_\gamma a \cdot [\gamma]
\]
\end{theorem}

\begin{proof}
The tower is constructed from the genus filtration on the bar complex.  By the modular operad decomposition (Theorem~\ref{thm:prism-higher-genus}), $\B(\cA) = \bigoplus_{g \geq 0} \B^{(g)}(\cA)$.  Define $\cA_g = \Omega(\bigoplus_{h \leq g} \B^{(h)}(\cA))$: the cobar construction applied to the genus-$\leq g$ truncation.  The inclusion $\bigoplus_{h \leq g} \B^{(h)} \hookrightarrow \bigoplus_{h \leq g+1} \B^{(h)}$ induces $\cA_g \to \cA_{g+1}$.  The connecting map adds the genus-$(g+1)$ correction: the new bar complex component $\B^{(g+1)}$ involves integration over $\overline{\mathcal{M}}_{g+1,n}$, and the correction term $\sum_\gamma \oint_\gamma a \cdot [\gamma]$ arises from the new homology cycles $\gamma \in H_1(\Sigma_{g+1})$ not present at lower genus.  The tower stabilizes for rational chiral algebras (finitely many modules, hence finite-dimensional conformal blocks at each genus) and converges to $\cA_\infty = \Omega(\B(\cA))$.
\end{proof}

\subsection{Spectral sequence convergence}

\begin{theorem}[Bar complex spectral sequence; \ClaimStatusProvedHere]
\label{thm:bar-complex-spectral-sequence}
\index{spectral sequence!bar-cobar|textbf}
There exists a spectral sequence:
\[E_2^{p,q} = H^p(\ConfigSpace{*}, H^q(\mathcal{A}^{\boxtimes *})) \Rightarrow H^{p+q}(\barBgeom(\mathcal{A}))\]
which converges under the following conditions:
\begin{enumerate}
\item $\mathcal{A}$ is bounded below: $\mathcal{A}_i = 0$ for $i < i_0$
\item The configuration spaces have finite cohomological dimension
\item The chiral algebra has finite homological dimension
\end{enumerate}
\end{theorem}

\begin{proof}
We filter the bar complex by configuration degree:
\[F_p\barBgeom(\mathcal{A}) = \bigoplus_{n \leq p} \barBgeom^n(\mathcal{A})\]

This gives a bounded filtration: $F_{-1} = 0$ (no negative configurations) and $F_p/F_{p-1} = \barBgeom^p(\mathcal{A})$ (single configuration degree).

The associated graded:
\[\text{Gr}_p = F_p/F_{p-1} \cong \Omega^*(\ConfigSpace{p+1}) \otimes \mathcal{A}^{\boxtimes(p+1)}\]

The $E_1$ page:
\[E_1^{p,q} = H^q(\text{Gr}_p) = H^q\!\left(\Omega^*(\ConfigSpace{p+1}) \otimes \mathcal{A}^{\boxtimes(p+1)}\right)\]

The $d_1$ differential is induced by $d_{\text{fact}}$:
\[d_1: E_1^{p,q} \to E_1^{p+1,q}\]

\emph{Convergence}: The spectral sequence converges because:
\begin{enumerate}
\item \emph{First quadrant}: $E_2^{p,q} = 0$ for $p < 0$ or $q < 0$
\item \emph{Bounded above}: For fixed total degree $n = p + q$, only finitely many $(p,q)$ contribute
\item \emph{Regular}: The filtration is exhaustive and Hausdorff
\end{enumerate}

Therefore:
\[E_\infty^{p,q} = \text{Gr}_p H^{p+q}(\barBgeom(\mathcal{A}))\]

The convergence is strong (not just weak) when $\mathcal{A}$ has finite homological dimension.
\end{proof}

\begin{corollary}[Degeneration {\cite{BGS96}}; \ClaimStatusProvedElsewhere]
\label{cor:spectral-degeneration}
\index{$E_2$ collapse}
If $\mathcal{A}$ is Koszul (Definition~\ref{def:chiral-koszul-pair}), the spectral sequence degenerates at $E_2$:
\[E_2^{p,q} = E_\infty^{p,q}\]
This gives:
\[H^n(\barBgeom(\mathcal{A})) = \bigoplus_{p+q=n} H^p(\ConfigSpace{*}) \otimes H^q(\mathcal{A}^!)\]
where $\mathcal{A}^!$ is the Koszul dual.
\end{corollary}

\subsection{Essential image of the bar functor}

\begin{theorem}[Complete essential image characterization; \ClaimStatusProvedHere]
\label{thm:essential-image-bar}
The essential image of the bar functor 
\[\barBgeom\colon \mathrm{ChirAlg}_X \to \mathrm{Coalg}_{\mathrm{conilp}}^{\mathrm{ch}}\]
consists precisely of those conilpotent chiral coalgebras $\mathcal{C}$ satisfying:
\begin{enumerate}
\item \emph{Logarithmic structure}: The coderivation $\delta: \mathcal{C} \to \mathcal{C}^{\otimes 2}$ has logarithmic singularities
\item \emph{Support condition}: $\text{supp}(\delta) \subset \bigcup_{i<j} D_{ij}$
\item \emph{Residue formula}: At $D_{ij}$:
\[\text{Res}_{D_{ij}}[\delta(c)] = \mu_{ij}^* \otimes c\]
where $\mu_{ij}^*$ is dual to chiral multiplication
\item \emph{Arnold relations}: The logarithmic coefficients satisfy the Arnold--Orlik--Solomon relations
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Necessity}: Let $\mathcal{C} = \barBgeom(\mathcal{A})$ for some chiral algebra $\mathcal{A}$.

(1) The coderivation is:
\[\delta = (d_{\text{fact}})^*: \barBgeom^n(\mathcal{A}) \to \barBgeom^{n+1}(\mathcal{A})\]

This is given by residues at collision divisors, hence has logarithmic singularities.

(2) The support is exactly $\bigcup_{i<j} D_{ij}$ by construction.

(3) The residue formula follows from the definition of $d_{\text{fact}}$.

(4) The Arnold relations are satisfied by logarithmic forms on configuration spaces.

\emph{Sufficiency}: Given $\mathcal{C}$ satisfying (1)-(4), we reconstruct $\mathcal{A}$.

Define $\mathcal{A} = \Omegach(\mathcal{C})$ (cobar construction). We need to show:
\[\mathcal{C} \cong \barBgeom(\Omegach(\mathcal{C}))\]

The isomorphism is constructed by reading each axiom as a construction step: logarithmic structure determines integration kernels, the support condition ensures locality, the residue formula recovers the OPE, and the Arnold relations ensure associativity.

If $\mathcal{C}$ satisfies (1)--(4), then $\Omegach(\mathcal{C})$ is a chiral algebra with:
\[\phi_i(z)\phi_j(w) = \text{Res}_{D_{ij}}[\delta(\phi_i \otimes \phi_j)]\]

The reconstruction map:
\[\Phi: \mathcal{C} \to \barBgeom(\Omegach(\mathcal{C}))\]
is given by:
\[\Phi(c) = \int_{\ConfigSpace{n}} c \wedge K_n\]
where $K_n$ is the universal kernel determined by the logarithmic structure.

This is an isomorphism by:
\begin{enumerate}
\item Injectivity: The logarithmic structure uniquely determines $c$
\item Surjectivity: Every bar element arises from some $c \in \mathcal{C}$
\item Preserves coalgebra structure: By compatibility of residues
\end{enumerate}
\end{proof}

\begin{corollary}[Recognition principle; \ClaimStatusProvedHere]
\label{cor:recognition-principle}
A chiral coalgebra $\mathcal{C}$ is in the essential image of $\barBgeom$ if and only if its cobar $\Omegach(\mathcal{C})$ is a chiral algebra (not just $A_\infty$).
\end{corollary}
\begin{proof}
The bar-cobar adjunction (Theorem~\ref{thm:bar-cobar-adjunction})
provides unit and counit maps for any augmented chiral algebra and
any conilpotent coalgebra.  On the Koszul locus
(Definition~\ref{def:chiral-koszul-pair}), the counit
$\bar{B}(\Omega(\mathcal{C})) \to \mathcal{C}$ is a
quasi-isomorphism (Theorem~\ref{thm:bar-cobar-isomorphism-main}),
which identifies $\mathcal{C}$ as the bar of its cobar.
This holds precisely when $\Omega(\mathcal{C})$ has strict
(not homotopy) chiral algebra structure.
\end{proof}

\subsection{BRST cohomology and string theory connection}

\begin{conjecture}[BRST cohomology realization; \ClaimStatusHeuristic]\label{conj:brst-cohomology}
The bar complex differential is isomorphic to the BRST operator of string theory:
\[\barBgeom(\mathcal{A}) \cong \text{Ker}(Q_{\text{BRST}})/\text{Im}(Q_{\text{BRST}})\]
where $Q_{\text{BRST}}$ is the BRST charge of the corresponding string theory.

The isomorphism is given by:
\begin{align}
Q_{\text{BRST}} &\leftrightarrow d_{\text{bar}} = d_{\text{int}} + d_{\text{fact}} + d_{\text{config}} \\
\text{Ghost number} &\leftrightarrow \text{Homological degree} \\
\text{Physical states} &\leftrightarrow \text{Bar cohomology classes}
\end{align}
\end{conjecture}

\begin{remark}[Physical motivation: string field theory]
The correspondence follows from the identification:

\emph{Step 1: String Field Theory.} The string field $\Psi$ satisfies the BRST equation:
\[Q_{\text{BRST}} \Psi + \Psi \star \Psi = 0\]
where $\star$ is the string product.

\emph{Step 2: Chiral Algebra Correspondence.} The string field decomposes as:
\[\Psi = \sum_{n=0}^\infty \Psi^{(n)} \otimes \omega^{(n)}\]
where $\Psi^{(n)} \in \mathcal{A}^{\otimes n}$ and $\omega^{(n)} \in \Omega^n(\overline{C}_n(X))$.

\emph{Step 3: BRST Action.} The BRST operator acts as:
\begin{align}
Q_{\text{BRST}}(\Psi^{(n)} \otimes \omega^{(n)}) &= \sum_{i=1}^n Q_i(\Psi^{(n)}) \otimes \omega^{(n)} \\
&\quad + \sum_{i<j} \mu_{ij}(\Psi^{(n)}) \otimes \text{Res}_{D_{ij}}[\omega^{(n)}] \\
&\quad + \Psi^{(n)} \otimes d_{\text{config}}\omega^{(n)}
\end{align}

This exactly matches the bar differential $d = d_{\text{int}} + d_{\text{fact}} + d_{\text{config}}$.

\emph{Step 4: Cohomology.} Physical states are BRST-closed but not exact:
\[H^*_{\text{BRST}} = \text{Ker}(Q_{\text{BRST}})/\text{Im}(Q_{\text{BRST}}) \cong H^*(\barBgeom(\mathcal{A}))\]
\end{remark}

\begin{example}[Bosonic string theory]
For the bosonic string with central charge $c = 26$:

\emph{Ghost System.} The $(b,c)$ ghost system has OPE:
\[b(z)c(w) \sim \frac{1}{z-w}\]

\emph{BRST charge.} 
\[Q_{\text{BRST}} = \oint dz \left[ c(z)T(z) + \frac{1}{2}:c(z)\partial c(z)b(z): \right]\]

\emph{Bar complex.} The geometric bar complex computes:
\[\barBgeom(\text{Vir}_{26} \otimes \text{ghosts}) \cong \text{String field theory}\]

\emph{Cohomology.} Physical states correspond to bar cohomology classes of weight $(1,1)$.
\end{example}

\begin{example}[Superstring theory]
For the superstring with central charge $c = 15$:

\emph{Superghost system.} The $(\beta,\gamma)$ system has OPE:
\[\beta(z)\gamma(w) \sim \frac{1}{z-w}\]

\emph{BRST charge.}
\[Q_{\text{BRST}} = \oint dz \left[ \gamma(z)G(z) + \frac{1}{2}:\gamma(z)\partial\gamma(z)\beta(z): \right]\]

\emph{Bar complex.} The geometric bar complex includes both NS and R sectors:
\[\barBgeom(\mathcal{A}_{\text{NS}} \oplus \mathcal{A}_{\text{R}}) \cong \text{Superstring field theory}\]

\emph{GSO Projection.} The bar complex automatically implements the GSO projection through the fermionic constraints.
\end{example}

\begin{conjecture}[Anomaly cancellation for matter-ghost systems; \ClaimStatusHeuristic]\label{conj:anomaly-cancellation}
For the \emph{coupled matter-ghost BRST system} in string theory, the geometric bar complex provides a geometric interpretation of anomaly cancellation:

\begin{enumerate}
\item \emph{Central Charge Constraint:} The \emph{BRST} differential of the combined matter-ghost system satisfies $d_{\text{BRST}}^2 = 0$ if and only if $c_{\text{matter}} = 26$ (bosonic) or $c_{\text{matter}} = 15$ (superstring).

\item \emph{Modular Invariance:} The bar complex of the total system transforms covariantly under $\operatorname{SL}_2(\mathbb{Z})$ if and only if the anomaly polynomial vanishes.

\item \emph{Geometric interpretation.} The anomaly corresponds to the obstruction to extending the bar complex of the total system to higher genus.
\end{enumerate}

\begin{remark}
This is \emph{not} in contradiction with the fact that the bar differential $d_{\text{bar}}^2 = 0$ for any individual chiral algebra (Theorem~\ref{thm:bar-nilpotency-complete}). The bar differential of each chiral algebra squares to zero by the Arnold relations. The BRST anomaly arises when one couples a matter chiral algebra to a ghost system and requires the \emph{total} BRST charge to be nilpotent; this imposes $c_{\text{total}} = c_{\text{matter}} + c_{\text{ghost}} = 0$.
\end{remark}
\end{conjecture}

\begin{remark}[Physical motivation: configuration space geometry]
The anomaly arises from the failure of the \emph{total BRST differential} (not the individual bar differential) to square to zero on the compactified configuration space.

\emph{Step 1: Individual Nilpotency.} On any chiral algebra, the bar differential satisfies $d_{\text{bar}}^2 = 0$ by Theorem~\ref{thm:bar-nilpotency-complete}.

\emph{Step 2: BRST Coupling.} The total BRST differential $d_{\text{BRST}} = d_{\text{matter}} + d_{\text{ghost}} + d_{\text{coupling}}$ includes a coupling term from the matter-ghost interaction. The cross-terms yield:
\[d_{\text{BRST}}^2 = \frac{c_{\text{matter}} + c_{\text{ghost}}}{24} \cdot \chi(\overline{C}_n(X))\]
where $\chi$ is the Euler characteristic.

\emph{Step 3: Cancellation.} The anomaly vanishes precisely when $c_{\text{matter}} + c_{\text{ghost}} = 0$. Since $c_{\text{ghost}} = -26$ (bosonic) or $c_{\text{ghost}} = -15$ (superstring), this forces $c_{\text{matter}} = 26$ or $c_{\text{matter}} = 15$ respectively.
\end{remark}

\begin{remark}
The geometric bar complex connects BRST cohomology (string theory), OPEs as residues on configuration spaces (conformal field theory), geometric constraints on the central charge (anomaly cancellation), and compatibility with genus-one geometry (modular invariance).
\end{remark}

\section{Relationship between bar-cobar and Koszul duality}

For a chiral Koszul pair $(\cA_1, \cA_2)$, the bar of one is the
Koszul dual coalgebra of the other, and Verdier duality on
$\operatorname{Ran}(X)$ provides the equivalence.  The Koszul
property --- diagonal Ext vanishing in the (bar degree, weight)
bigrading --- is the condition under which this equivalence descends
from the coderived category to the ordinary derived category.

\subsection{Precise formulation of the relationship}

\begin{remark}[Criteria for chiral Koszul pairs --- updated recollection]\label{rem:koszul-criteria}
\label{rem:koszul-chiral}
\index{Koszul duality!chiral}
\index{Koszul property}
Recall from Definition~\ref{def:chiral-koszul-pair} that a chiral Koszul pair
is specified by antecedent recognition data: a chiral twisting datum, a Koszul
twisting morphism, compatible filtrations, and Verdier-compatible dual coalgebras.
The bar/cobar quasi-isomorphisms are then proved consequences
(Theorem~\ref{thm:fundamental-twisting-morphisms} and
Theorem~\ref{thm:bar-cobar-isomorphism-main}), not part of the definition.
\end{remark}

\begin{remark}[Bar-cobar vs.\ Koszul: the fundamental distinction]\label{rem:fundamental-distinction}
\emph{Always true (for any augmented chiral algebra $\mathcal{A}$):}
\begin{itemize}
\item $\bar{B}: \mathcal{A} \to \bar{B}(\mathcal{A})$ exists and $d^2 = 0$
  (Theorem~\ref{thm:bar-nilpotency-complete})
\item $\Omega: \bar{B}(\mathcal{A}) \to \Omega(\bar{B}(\mathcal{A}))$ exists
  and $d^2 = 0$
  (Theorem~\ref{thm:cobar-d-squared-zero})
\end{itemize}

These are \emph{constructions}---they work for any augmented algebra.

\emph{On the Koszul locus only
  \textup{(}chiral Koszul pairs,
  Definition~\textup{\ref{def:chiral-koszul-pair}):}}
\begin{itemize}
\item The counit $\Omega(\bar{B}(\mathcal{A})) \xrightarrow{\sim} \mathcal{A}$
  is a quasi-isomorphism (Theorem~\ref{thm:bar-cobar-isomorphism-main})
\item $\bar{B}(\mathcal{A}_1) \simeq \mathcal{A}_2^!$ as chiral coalgebras
  (Theorem~\ref{thm:bar-concentration})
\end{itemize}

Off the Koszul locus, $\Omega(\bar{B}(\mathcal{A}))$ still exists but
the counit need not be a quasi-isomorphism; the bar-cobar object
represents $\mathcal{A}$ in the completed coderived category
$D^{\mathrm{co}}(\text{-}\mathrm{CoMod})$ of Positselski
(Theorem~\ref{thm:higher-genus-inversion}(b)).
\end{remark}

\begin{theorem}[Necessary conditions for chiral Koszul duality {\cite{FG12}}; \ClaimStatusProvedElsewhere]\label{thm:koszul-necessary}
For $(\mathcal{A}_1, \mathcal{A}_2)$ to form a chiral Koszul pair, the following must hold:
\begin{enumerate}
\item Both algebras are finitely generated over $\mathcal{D}_X$
\item The bar complexes have finite-dimensional cohomology in each degree
\item There exists a non-degenerate pairing $\langle -, - \rangle: \bar{B}(\mathcal{A}_1) \otimes \bar{B}(\mathcal{A}_2) \to \omega_X$
\end{enumerate}
\end{theorem}

\subsection{Diagram of relationships}

The relationship between bar, cobar, and Koszul duality can be summarized:

\begin{center}
\begin{tikzcd}[column sep=huge, row sep=huge]
\mathcal{A}_1 \arrow[r, "\bar{B}", "{\text{(algebra → coalgebra)}}"'] 
  \arrow[d, shift left=2, "\text{Koszul}", "{\text{duality}}"' {description}] 
  & \bar{B}(\mathcal{A}_1) \arrow[r, "\simeq", "{\text{(when Koszul pair)}}"'] 
  & \mathcal{A}_2^! \\
\mathcal{A}_2 \arrow[u, shift left=2] 
  \arrow[r, "\bar{B}"', "{\text{(algebra → coalgebra)}}"'] 
  & \bar{B}(\mathcal{A}_2) \arrow[r, "\simeq"', "{\text{(symmetric)}}"'] 
  & \mathcal{A}_1^! \arrow[ull, "\Omega"', bend right=20, "{\text{(coalgebra → algebra)}}"' {description}]
\end{tikzcd}
\end{center}

\emph{Reading the diagram.}
\begin{itemize}
\item Horizontal arrows ($\bar{B}$): Constructions that always exist
\item Vertical double arrow: Koszul duality (exists only for special pairs)
\item Horizontal equivalences ($\simeq$): The Koszul condition
\item Curved arrow ($\Omega$): Cobar reconstruction completing the cycle
\end{itemize}

\subsection{Examples illustrating the distinction}

\begin{example}[Heisenberg: level shift required]\label{ex:heisenberg-koszul-vs-barcobar}
Bar-cobar inversion gives $\Omega(\bar{B}(\mathcal{H}_k)) \simeq \mathcal{H}_k$ automatically, while Koszul duality yields $\mathcal{H}_k^! \simeq \mathrm{Sym}^{\mathrm{ch}}(V^*)$ with curvature $m_0 = -k\,\omega$ (cf.\ \S\ref{sec:heisenberg-koszul}).  These are distinct statements: bar-cobar inverts $\mathcal{H}_k$, but the Koszul dual is a different type of algebra (commutative vs.\ Lie).  See Part~II.
\end{example}

\section{Curved Koszul duality and quantum obstructions}
\label{sec:curved-koszul-quantum}

\begin{theorem}[Quantum deformation-obstruction complementarity; \ClaimStatusProvedElsewhere]\label{thm:deformation-obstruction}
\textup{[Regime: curved-central on the Koszul locus; all genera
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

For a chiral algebra $\mathcal{A}$ on a curve $X$, the genus-$g$ quantum corrections
satisfy:
\[Q_g(\mathcal{A}) \oplus Q_g(\mathcal{A}^!) \simeq H^*(\mathcal{M}_g, Z(\mathcal{A}))\]
where:
\begin{itemize}
\item $Q_g(\mathcal{A})$ = space of genus-$g$ obstructions to Koszul duality
\item $Q_g(\mathcal{A}^!)$ = space of genus-$g$ deformations of the dual algebra
\item $Z(\mathcal{A})$ = center of $\mathcal{A}$
\item $H^*(\mathcal{M}_g, Z(\mathcal{A}))$ = cohomology of moduli space with coefficients in center
\end{itemize}
\end{theorem}

\begin{proof}[Proof (outline; full proof in \S\textup{\ref{sec:complementarity-theorem}})]
The complete proof, synthesizing five lemmas via the Verdier
involution~$\sigma$ and the genus spectral sequence, is given in
Theorem~\ref{thm:quantum-complementarity-main}.

\emph{Foundation: Curved $A_\infty$ Structures}

Following Gui--Li--Zeng~\cite{GLZ22}, a curved chiral algebra $\mathcal{A}$ has:
\begin{enumerate}
\item Multiplication: $\mu_2: \mathcal{A}^{\otimes 2} \to \mathcal{A}$
\item Higher operations: $\mu_n: \mathcal{A}^{\otimes n} \to \mathcal{A}$ for $n \geq 3$
\item Curvature: $\mu_0: \mathbb{C} \to \mathcal{A}$
\end{enumerate}
satisfying the curved $A_\infty$ relations:
\[\sum_{\substack{r+s+t=n \\ r,t \geq 0,\; s \geq 0}} (-1)^{rs+t}\, \mu_{r+1+t}(\mathrm{id}^{\otimes r} \otimes \mu_s \otimes \mathrm{id}^{\otimes t}) = 0\]

For $n=0$: $\mu_1(\mu_0) = 0$ (the curvature element is a $\mu_1$-cycle).

For $n=1$: $\mu_1^2 = [\mu_0, -]_{\mu_2}$, so $\mu_1$ is a differential only modulo curvature.

\emph{Step 1: Genus Stratification of Obstructions}

\noindent
\textbf{Notation.}
The differential $\dfib$ denotes the \emph{fiberwise} bar differential at
genus~$g$: the collision-residue differential on a fixed curve~$\Sigma_g$.
It is generically \emph{curved} ($\dfib^{\,2} \neq 0$).
The total corrected differential $\Dg{g}$, which incorporates period
corrections to restore strict nilpotence ($\Dg{g}^{\,2} = 0$), is
introduced in Convention~\ref{conv:higher-genus-differentials}.

\medskip

The failure of the fiberwise bar differential to square to zero is measured by:
\[\dfib^{\,2}: \bar{B}^n_g(\mathcal{A}) \to \bar{B}^{n+2}_g(\mathcal{A})\]

\begin{lemma}[Obstruction cohomology class {\cite{Positselski11}}; \ClaimStatusProvedElsewhere]\label{lem:obstruction-class}
The composition $\dfib^{\,2}$ defines a cohomology class:
\[[\dfib^{\,2}] \in H^2(\bar{B}_g(\mathcal{A}), Z(\mathcal{A}))\]
which vanishes if and only if the genus-$g$ bar construction is well-defined.
\end{lemma}

\begin{proof}
In the CDG framework (Definition~\ref{def:chiral-CDG-coalgebra}), the genus-$g$
bar complex carries curvature $h = m_0^{(g)}$ satisfying $\dfib^{\,2} = h \ast (-)$.
Explicitly, $m_0^{(g)}$ is the genus-$g$ contribution to the bar curvature,
constructed as a fiber integral:
\[
m_0^{(g)} = \int_{\Sigma_g} \omega_g \in \bar{B}^0_g(\mathcal{A}),
\]
where $\omega_g$ is the volume form of the genus-$g$ propagator
(cf.\ Definition~\ref{def:genus-stratified-bar}).

\emph{Centrality.}
The element $m_0^{(g)}$ lies in the center $Z(\mathcal{A})$ by the
following chain-level argument.  For any generator $a \in \mathcal{A}$,
the OPE $m_0^{(g)}{}_{(n)} a$ for $n \geq 0$ vanishes because $m_0^{(g)}$
has conformal weight~$0$ (it is a scalar on each conformal-weight space),
and the Borcherds identity forces the iterated residue
$[\mathrm{Res}_{D_{ij}}, \mathrm{Res}_{D_{kl}}]$ to act trivially on
generators when $D_{ij} \cap D_{kl} = \emptyset$ (factorization axiom),
while nested collisions contribute only scalar multiples (OPE associativity).

\emph{Cocycle condition.}
The curved $A_\infty$ relation at $n=0$
(Definition~\ref{def:curved-ainfty}) gives
$\mu_1(m_0^{(g)}) = 0$, so $m_0^{(g)}$ is a $d$-cocycle.  The map
$\phi \mapsto m_0^{(g)} \ast \phi$ therefore defines a $2$-cocycle in
the Hochschild complex $C^2(\bar{B}_g(\mathcal{A}), Z(\mathcal{A}))$,
and the class $[\dfib^{\,2}] = [m_0^{(g)} \ast (-)]$ is the obstruction to
lifting the genus-$0$ differential (where $m_0^{(0)} = 0$) to genus~$g$.
It vanishes if and only if $m_0^{(g)} = d(\text{something})$, i.e., the
curvature is exact---which is the CDG condition for the bar construction
to be well-defined as a DG object rather than merely CDG.
See the full spectral sequence analysis in the proof of
Theorem~\ref{thm:quantum-complementarity-main}.
\end{proof}

\emph{Step 2: Moduli space interpretation.}

The genus-$g$ corrections are parametrized by $H^*(\mathcal{M}_g, \mathcal{Z}(\mathcal{A}))$ (cohomology with coefficients in the center).  The connection comes from period integrals:

\begin{lemma}[Period integral formula {\cite{Fay73}}; \ClaimStatusProvedElsewhere]\label{lem:period-integral}
For $\omega \in \Omega^1(\overline{\mathcal{M}}_g)$, the genus-$g$ obstruction is:
\[\mathrm{Obs}_g(\omega) = \int_{\mathcal{C}_g} \omega \wedge
\left(\sum_{\text{cycles}} \mathrm{Res}_{D_i} \wedge \mathrm{Res}_{D_j}\right)\]
where the integral is over the universal curve $\mathcal{C}_g \to \overline{\mathcal{M}}_g$.
\end{lemma}

\begin{proof}
The fiberwise bar differential at genus~$g$ is
$\dfib = \sum_{D \subset \partial \overline{C}_n(\Sigma_g)} \mathrm{Res}_D$,
constructed from logarithmic propagators
$\omega_{ij} = d\log(z_i - z_j)$ on configuration spaces
(Definition~\ref{def:bar-differential-complete}).  We compute $\dfib^{\,2}$ at the
cochain level.

\emph{Step~1: Double residue as fiber $2$-form.}
For $\phi \in \bar{B}^n_g(\mathcal{A})$, the composition $\dfib^{\,2}(\phi)$
is a sum of double residues $\mathrm{Res}_{D_i} \circ \mathrm{Res}_{D_j}$
over pairs of boundary divisors.  When $D_i \cap D_j = \emptyset$
(disjoint collisions), the residues commute and cancel pairwise
(cf.\ the anticommutator $\{d_{\mathrm{fact}}, d_{\mathrm{config}}\} = 0$
of Theorem~\ref{thm:chiral-hochschild-differential}).
The surviving terms come from nested collisions $D_i \subset D_j$,
producing a $2$-form kernel $K_{ij}^{(g)}$ on~$\overline{C}_n(\Sigma_g)$.
By Lemma~\ref{lem:obstruction-class}, this kernel takes values
in~$Z(\mathcal{A})$.

\emph{Step~2: Fiber integration.}
Consider the universal family
$\pi\colon \overline{C}_n(\mathcal{C}_g) \to \overline{\mathcal{M}}_g$.
The pushforward $\pi_*(K_{ij}^{(g)})$ is a section of
$\mathcal{Z}(\mathcal{A})$ on $\overline{\mathcal{M}}_g$---the
fiber integral of the double-residue kernel.  Evaluating against
$\omega \in \Omega^1(\overline{\mathcal{M}}_g)$ gives:
\[
\mathrm{Obs}_g(\omega)
= \int_{\overline{\mathcal{M}}_g} \omega \wedge \pi_*\!\left(
\sum_{i < j} K_{ij}^{(g)}\right)
= \int_{\mathcal{C}_g} \omega \wedge
\sum_{\text{cycles}} \mathrm{Res}_{D_i} \wedge \mathrm{Res}_{D_j},
\]
where the second equality is the projection formula.

\emph{Step~3: Boundary vanishing.}
The boundary contributions from $\partial\overline{C}_n(\Sigma_g)$
vanish fiberwise: on each fiber $\overline{C}_n(\Sigma_g)$, the
Arnold relations (Theorem~\ref{thm:arnold-three}) ensure
$\omega_{ij} \wedge \omega_{jk} + \omega_{jk} \wedge \omega_{ki}
+ \omega_{ki} \wedge \omega_{ij} = 0$, which forces the boundary
integral to cancel term by term.
The detailed bookkeeping across all boundary strata is carried out in
the proof of Theorem~\ref{thm:quantum-complementarity-main},
Steps~3--4.
\end{proof}

\emph{Step 3: Dual Deformations}

Now consider the Koszul dual $\mathcal{A}^!$. Its genus-$g$ structure is given by 
the cobar construction:
\[\Omega_g(\mathcal{A}^!) = \text{Sym}(\mathcal{A}^![1])\]
with differential induced from the coproduct $\Delta: \mathcal{A}^! \to 
\mathcal{A}^! \otimes \mathcal{A}^!$.

\begin{lemma}[Deformation space; \ClaimStatusProvedHere]\label{lem:deformation-space}
The genus-$g$ deformations of $\mathcal{A}^!$ are parametrized by a summand of the cohomology with coefficients in the center:
\[\mathrm{Def}_g(\mathcal{A}^!) \hookrightarrow H^*(\overline{\mathcal{M}}_g, \mathcal{Z}(\mathcal{A}))\]
\end{lemma}

\begin{proof}
A genus-$g$ deformation of $\mathcal{A}^!$ is a flat family
$\tilde{\mathcal{A}}^! \to \overline{\mathcal{M}}_g$ with fiber at a
basepoint equal to $\mathcal{A}^!$.  Infinitesimally, such deformations
are classified by
$H^1(\overline{\mathcal{M}}_g, \underline{\mathrm{End}}(\mathcal{A}^!))$,
where $\underline{\mathrm{End}}(\mathcal{A}^!)$ is the local system of
endomorphisms.

\emph{Chain-level identification.}
By the bar-cobar adjunction
(Proposition~\ref{prop:cobar-bar-augmentation}), the endomorphism
complex of $\mathcal{A}^!$ is quasi-isomorphic to the CDG Hom-complex
(Proposition~\ref{prop:cdg-hom-complex}):
\[
\underline{\mathrm{End}}(\mathcal{A}^!)
\;\simeq\;
\underline{\mathrm{Hom}}_C^{\mathrm{ch}}(\mathcal{A}^!, \mathcal{A}^!).
\]
The degree-$0$ cohomology of this complex is
$HH^0(\mathcal{A}^!) = Z(\mathcal{A}^!)$.  By Koszul duality
(Theorem~\ref{thm:chiral-koszul-duality}), the center local system
satisfies $\mathcal{Z}(\mathcal{A}^!) \cong \mathcal{Z}(\mathcal{A})$
(the bar-cobar involution preserves centers).  Hence:
\[
\mathrm{Def}_g(\mathcal{A}^!)
= H^1(\overline{\mathcal{M}}_g, \mathcal{Z}(\mathcal{A}^!))
\hookrightarrow H^*(\overline{\mathcal{M}}_g, \mathcal{Z}(\mathcal{A})).
\]
\emph{(Note: One must use the local system $\mathcal{Z}(\mathcal{A})$,
not the trivial local system.  By Harer's theorem,
$H^1(\mathcal{M}_g, \mathbb{Q}) = 0$ for $g \geq 2$, so the
deformation space would be trivially zero with trivial coefficients.)}
\end{proof}

\emph{Step 4: Perfect Pairing}

\begin{lemma}[Obstruction-deformation pairing; \ClaimStatusProvedHere]\label{lem:obs-def-pairing}
There is a perfect pairing:
\[\langle -, - \rangle: Q_g(\mathcal{A}) \otimes Q_g(\mathcal{A}^!) \to
H^{3g-3}(\overline{\mathcal{M}}_g, \mathbb{C})\]
given by the trace:
\[\langle \mathrm{Obs}, \mathrm{Def} \rangle = \mathrm{Tr}(\mathrm{Obs} \circ \mathrm{Def}).\]
\end{lemma}

\begin{proof}
\emph{Step~1: Cochain-level pairing.}
At the cochain level, the Verdier duality involution $\sigma$
on the center local system $\mathcal{Z}(\mathcal{A})$
(Theorem~\ref{thm:verdier-bar-cobar}) induces an involution
$\sigma^*$ on $C^*(\overline{\mathcal{M}}_g, \mathcal{Z}(\mathcal{A}))$.
Define the pairing on cochains by:
\[
\langle \alpha, \beta \rangle_{\sigma}
:= \int_{\overline{\mathcal{M}}_g}
\mathrm{Tr}_{\mathcal{Z}(\mathcal{A})}(\alpha \wedge \sigma(\beta)),
\]
where $\mathrm{Tr}_{\mathcal{Z}(\mathcal{A})}$ is the trace on the
center.  This is well-defined because $\sigma$ is an isometry for the
Killing form on~$\mathcal{Z}(\mathcal{A})$ and the integral converges
on the compact orbifold $\overline{\mathcal{M}}_g$.

\emph{Step~2: Eigenspace decomposition.}
By Theorem~\ref{thm:quantum-complementarity-main}(ii), the Verdier
involution satisfies $\sigma^2 = \mathrm{id}$, so
$H^*(\overline{\mathcal{M}}_g, \mathcal{Z}(\mathcal{A}))$ decomposes
into $\pm 1$-eigenspaces:
$Q_g(\mathcal{A}) = \ker(\sigma - \mathrm{id})$ and
$Q_g(\mathcal{A}^!) = \ker(\sigma + \mathrm{id})$.
The pairing $\langle -, - \rangle_{\sigma}$ restricts to zero on
each eigenspace (since $\sigma(\beta) = \pm\beta$ and the
antisymmetry $\langle \alpha, \sigma\beta \rangle
= -\langle \sigma\alpha, \beta \rangle$ forces vanishing on
equal eigenvalues).

\emph{Step~3: Non-degeneracy.}
On the cross-terms $Q_g(\mathcal{A}) \otimes Q_g(\mathcal{A}^!)$,
the pairing reduces to Serre duality on $\overline{\mathcal{M}}_g$
with coefficients in $\mathcal{Z}(\mathcal{A})$.  Serre duality is
non-degenerate on the compact orbifold $\overline{\mathcal{M}}_g$,
so the pairing is perfect.
\end{proof}

\emph{Step 5: Center Cohomology}

\begin{lemma}[Center as obstruction-deformation space; \ClaimStatusProvedHere]\label{lem:center-cohomology}
The direct sum $Q_g(\mathcal{A}) \oplus Q_g(\mathcal{A}^!)$ naturally identifies with:
\[H^*(\overline{\mathcal{M}}_g, \mathcal{Z}(\mathcal{A}))\]
\end{lemma}

\begin{proof}
The Verdier involution $\sigma$ on the center local system
$\mathcal{Z}(\mathcal{A})$ is an involution ($\sigma^2 = \mathrm{id}$)
that acts on cohomology.  Since we work over~$\mathbb{C}$, the
eigenvalues of $\sigma^*$ on
$H^*(\overline{\mathcal{M}}_g, \mathcal{Z}(\mathcal{A}))$ are $\pm 1$,
giving a direct sum decomposition:
\[
H^*(\overline{\mathcal{M}}_g, \mathcal{Z}(\mathcal{A}))
= \ker(\sigma^* - \mathrm{id})
\oplus \ker(\sigma^* + \mathrm{id}).
\]
It remains to identify the two summands.

\emph{The $+1$-eigenspace is $Q_g(\mathcal{A})$.}
By Lemma~\ref{lem:obstruction-class}, the obstruction class
$[\dfib^{\,2}] = [m_0^{(g)} \ast (-)]$ lies in the $\sigma$-invariant part
of $H^*(\overline{\mathcal{M}}_g, \mathcal{Z}(\mathcal{A}))$, because
$\sigma(m_0^{(g)}) = m_0^{(g)}$ (the curvature is Verdier-self-dual:
it is constructed from the volume form $\omega_g$, which is a canonical
section of $K_{\Sigma_g}$, and Verdier duality acts as the identity on
canonical sections).  The full $+1$-eigenspace is generated by such
obstruction classes as $g$ varies, giving
$Q_g(\mathcal{A}) = \ker(\sigma^* - \mathrm{id})$.

\emph{The $-1$-eigenspace is $Q_g(\mathcal{A}^!)$.}
By Lemma~\ref{lem:deformation-space},
$\mathrm{Def}_g(\mathcal{A}^!)$ embeds in
$H^*(\overline{\mathcal{M}}_g, \mathcal{Z}(\mathcal{A}))$.
Since Koszul duality negates the Verdier involution
($\sigma_{\mathcal{A}^!} = -\sigma_{\mathcal{A}}$
on centers, by Theorem~\ref{thm:verdier-bar-cobar}),
deformation classes lie in the $-1$-eigenspace:
\[
Q_g(\mathcal{A}^!) = \ker(\sigma^* + \mathrm{id}).
\]

\emph{Exhaustion.}
Since $\ker(\sigma^* - \mathrm{id}) \oplus \ker(\sigma^* + \mathrm{id})$
is the full space (over~$\mathbb{C}$, any involution is diagonalizable),
the decomposition is exhaustive.
\end{proof}

\emph{Step 6: Conclusion}

Combining Lemmas \ref{lem:obstruction-class}, \ref{lem:period-integral}, 
\ref{lem:deformation-space}, \ref{lem:obs-def-pairing}, and \ref{lem:center-cohomology}, 
we conclude:
\[Q_g(\mathcal{A}) \oplus Q_g(\mathcal{A}^!) \simeq H^*(\mathcal{M}_g, Z(\mathcal{A}))\]
as claimed.

\end{proof}

\begin{remark}[Explicit formulas for low genus]\label{rem:explicit-low-genus-curved}

\emph{Genus 0.} $\mathcal{M}_0 = \text{pt}$, so $H^*(\mathcal{M}_0, Z(\mathcal{A})) 
= Z(\mathcal{A})$. There are no quantum corrections.

\emph{Genus 1.} The moduli space $\mathcal{M}_1$ has $H^1(\mathcal{M}_1, \mathbb{Q}) = 0$ (as for all $\mathcal{M}_g$), but $\dim \mathcal{M}_1 = 1$.  Quantum corrections enter through the \emph{partition function}, which depends on the modulus $\tau \in \mathfrak{h}/\mathrm{SL}_2(\mathbb{Z})$:
\[Q_1(\mathcal{H}_k) = \mathbb{C} \cdot k\]
where $k$ is the level of the Heisenberg algebra.  Here $Q_1$ is computed from the center $Z(\mathcal{A})$ evaluated over $\mathcal{M}_1$, not from $H^1$.

The dual deformation:
\[Q_1(\text{Sym}(V^*)) = \mathbb{C} \cdot [V^* \wedge V^*]\]
measures how the symmetric algebra deforms from genus 0 to genus 1.

\emph{Genus 2.} $\dim \mathcal{M}_2 = 3$ and $H^2(\mathcal{M}_2, \mathbb{Q}) = \mathbb{Q} \cdot \lambda_1$ (generated by the Hodge class). For $\widehat{\mathfrak{sl}}_2$ at
critical level, the obstructions are:
\[Q_2(\widehat{\mathfrak{sl}}_2) = \mathbb{C} \cdot \lambda_1 \oplus \mathbb{C} \cdot
[\alpha, \alpha]\]
where $\lambda_1 \in H^2(\mathcal{M}_2)$ is the first Hodge class and $[\alpha, \alpha]$
is the self-commutator of the simple root.
\end{remark}

\begin{corollary}[Curved differential formula; \ClaimStatusProvedHere]\label{cor:curved-differential}
For a curved chiral algebra $\mathcal{A}$ with curvature $\mu_0$, the fiberwise genus-$g$ bar
differential is:
\[\dfib = \dzero + \mu_0 \otimes \left(\int_{\mathcal{M}_g} \omega_g\right)\]
where $\omega_g \in H^*(\mathcal{M}_g, \mathcal{Z}(\mathcal{A}))$ is the quantum correction class (living in the cohomology of $\mathcal{M}_g$ with coefficients in the center $\mathcal{Z}(\mathcal{A})$).

This satisfies:
\[\dfib^{\,2} = [\mu_0, -] \otimes \left(\int_{\mathcal{M}_g} \omega_g^2\right)
\in H^*(\mathcal{M}_g, Z(\mathcal{A}))\]
which is the obstruction class.
\end{corollary}
\begin{proof}
The genus-$g$ bar differential receives quantum corrections from the
period matrix of the curve
(Theorem~\ref{thm:quantum-diff-squares-zero}).  When $\mathcal{A}$ has
nonzero curvature $m_0 = \mu_0(1) \in \mathcal{A}^2$, the correction
class $\omega_g$ lives in
$H^*(\mathcal{M}_g, \mathcal{Z}(\mathcal{A}))$ by
Theorem~\ref{thm:quantum-complementarity-main}.  Write
$\dfib = \dzero + m_0 \otimes \omega_g$, where the second term acts
via the inner derivation $[m_0, -]_{m_2}$ tensored with the modular
class.  Squaring:
\[
\dfib^{\,2}
= \underbrace{\dzero^2}_{=\,0}
+ \dzero(m_0 \otimes \omega_g)
+ (m_0 \otimes \omega_g)\dzero
+ (m_0 \otimes \omega_g)^2.
\]
The cross terms vanish: $\dzero(m_0) = m_1(m_0) = 0$ by the curved
$A_\infty$ relation at $n = 0$
(Theorem~\ref{thm:curvature-central}(1)), and
$(m_0 \otimes \omega_g) \circ \dzero$ vanishes on cocycles by the
same centrality.  The surviving term
$(m_0 \otimes \omega_g)^2 = [m_0, -]_{m_2} \otimes \omega_g^2$
uses the $n = 1$ curved $A_\infty$ relation $m_1^2 = [m_0, -]_{m_2}$
(Theorem~\ref{thm:curvature-central}(2)).
\end{proof}

\section{Curved Koszul duality and I-adic completion}
\label{sec:curved-koszul-i-adic}

Not all chiral algebras are quadratic. Many examples of interest---Virasoro, higher W-algebras, 
$W_\infty$---require curved structures or infinite-dimensional presentations. For these, 
the strict finite-type bar-cobar theorem no longer applies directly.  One must
separate the proved M-level completed shadows that control curvature and
complementarity from the stronger H-level realization problem for an actual dual
factorization object.  To treat even the model-level question, we must introduce:
\begin{itemize}
\item \emph{Curved structures}: Allowing μ₀ ≠ 0 (failure of d² = 0)
\item \emph{Completion}: I-adic topology ensuring convergence
\item \emph{Filtered structures}: More general than curved (Gui--Li--Zeng)
\end{itemize}

We follow Gui--Li--Zeng~\cite{GLZ22}.

\subsection{Curved $A_\infty$ algebras: definitions}
\label{sec:curved-ainfty-definition}

\begin{definition}[Curved \texorpdfstring{$A_\infty$}{A-infinity} algebra]
\label{def:curved-ainfty}
A \emph{curved $A_\infty$ algebra} is a graded vector space $A$ with operations:
\begin{equation}
\{\mu_n: A^{\otimes n} \to A\}_{n \geq 0}
\end{equation}
of degree $2-n$, satisfying the \emph{curved $A_\infty$ relations}:
\begin{equation}\label{eq:curved-ainfty-relations}
\sum_{\substack{r+s+t=n \\ r,t \geq 0,\; s \geq 0}} (-1)^{rs+t}\, \mu_{r+1+t}(\mathrm{id}^{\otimes r} \otimes \mu_s \otimes \mathrm{id}^{\otimes t}) = 0
\end{equation}

Key differences from ordinary $A_\infty$:
\begin{enumerate}
\item $n=0$ is allowed: $\mu_0: \mathbb{C} \to A$ is the \emph{curvature}
\item $n=1$: $\mu_1^2 = [\mu_0, -]$, so $\mu_1$ is a differential only modulo curvature
\item $n \geq 2$: Higher operations as usual
\end{enumerate}
\end{definition}

\begin{remark}[Curvature, backreaction, and \texorpdfstring{$d^2$}{d\textasciicircum 2}]\label{rem:curvature-backreaction-terminology}
\begin{enumerate}[label=(\roman*)]
\item The \emph{curvature} is $m_0 := \mu_0(1) \in A^2$.
\item $\mu_1^2(a) = \mu_2(m_0, a) - \mu_2(a, m_0)$: the total bar differential always satisfies $d_{\mathrm{bar}}^2 = 0$; curvature manifests in the \emph{internal} $A_\infty$ structure.
\item In physics, \emph{backreaction} is the same phenomenon: the BRST operator $Q = \mu_1$ satisfies $Q^2 \neq 0$, with the obstruction measured by $m_0$.
\item A curved $A_\infty$ algebra is \emph{strictifiable} iff $m_0$ is central (Theorem~\ref{thm:curvature-central}) and the curvature class is gauge-trivial in the completed filtration.
\end{enumerate}
\end{remark}

\begin{theorem}[Curvature as \texorpdfstring{$\mu_1$}{mu1}-cycle; \ClaimStatusProvedHere]
\label{thm:curvature-central}
For a curved $A_\infty$ algebra $(A, \mu_0, \mu_1, \mu_2, \ldots)$, the curvature element satisfies:
\begin{enumerate}
\item $\mu_1(\mu_0) = 0$ \quad (the curvature is a $\mu_1$-cycle);
\item $\mu_1^2 = [\mu_0, -]_{\mu_2}$, where $[\mu_0, a]_{\mu_2} := \mu_2(\mu_0, a) - \mu_2(a, \mu_0)$ is the inner derivation.
\end{enumerate}
In particular, $\mu_1$ fails to be a differential precisely when $\mu_0$ is \emph{not} central with respect to $\mu_2$.  For chiral algebras (which are graded-commutative), $[\mu_0, -]_{\mu_2} = 0$ automatically, so the curvature enters through higher operations ($\mu_3, \mu_4, \ldots$) or via the completed tensor product.
\end{theorem}

\begin{proof}
The curved $A_\infty$ relations $\sum_{r+s+t=n}(-1)^{rs+t}\mu_{r+1+t}(\mathrm{id}^{\otimes r}\otimes \mu_s \otimes \mathrm{id}^{\otimes t})=0$ give, at each level:
\begin{itemize}
\item $n=0$: $\mu_1(\mu_0) = 0$ \quad (the curvature is a $\mu_1$-cycle).
\item $n=1$: $\mu_1^2(a) - \mu_2(\mu_0, a) + \mu_2(a, \mu_0) = 0$ for all $a$ \quad (failure of $\mu_1^2 = 0$).
\end{itemize}

Rearranging the $n=1$ relation: $\mu_1^2(a) = \mu_2(\mu_0, a) - \mu_2(a, \mu_0) = [\mu_0, a]_{\mu_2}$.

The $n=2$ relation (Leibniz rule for $\mu_1$ acting on $\mu_2$) applied using $\mu_1(\mu_0) = 0$ from $n=0$ gives:
\begin{equation}
\mu_1(\mu_2(\mu_0, a)) = \mu_2(\mu_0, \mu_1(a))
\end{equation}
confirming that the inner derivation $[\mu_0, -]_{\mu_2}$ commutes with $\mu_1$, as required for the self-consistency of the curved structure.
\end{proof}

\subsection{I-adic completion: topology and convergence}
\label{sec:i-adic-completion}

\begin{definition}[I-adic topology]
\label{def:i-adic-topology}
\index{nilpotent completion}
Let $A$ be a curved $A_\infty$ algebra with augmentation ideal $I = \ker(\varepsilon: A \to \mathbb{C})$.

The \emph{I-adic completion} of $A$ is:
\begin{align}
\hat{A} &:= \varprojlim_n A/I^n \notag \\
  &= \bigl\{a \in {\textstyle\prod_{n \geq 0}} A/I^n :
  \text{compatible}\bigr\}.
\end{align}

An element $a \in \hat{A}$ can be written as a formal series:
\begin{equation}
a = a_0 + a_1 + a_2 + \cdots \quad \text{where } a_n \in I^n/I^{n+1}
\end{equation}
\end{definition}

\begin{theorem}[When completion is necessary; \ClaimStatusProvedElsewhere]
\label{thm:completion-necessity}
Completion $A \to \hat{A}$ is necessary when:
\begin{enumerate}
\item \emph{Infinite sums}: Operations μₙ produce infinite sums not convergent in $A$
\item \emph{Non-conilpotent}: Bar complex $\bar{B}(A)$ is not conilpotent
\item \emph{Non-quadratic}: Relations involve infinitely many generators
\end{enumerate}

For example, the Virasoro algebra and $W_\infty$ need completion, while Heisenberg and Kac--Moody (conilpotent) do not.
\emph{More precisely:} Virasoro admits a completed same-family shadow used
throughout Parts~II--III, whereas $W_\infty$ marks the frontier where a
completed duality theorem is still missing.
\end{theorem}

\begin{proof}[Proof by Example: Virasoro]
The Virasoro algebra has generators $\{L_n\}_{n \in \mathbb{Z}}$ with:
\begin{equation}
[L_m, L_n] = (m-n)L_{m+n} + \frac{c}{12}m(m^2-1)\delta_{m+n,0}
\end{equation}

Consider the bar complex element:
\begin{equation}
\omega = L_0 \otimes L_0 \in \bar{B}^2(\text{Vir})
\end{equation}

Applying the differential involves summing over all intermediate states:
\begin{equation}
d(\omega) = \sum_{k \in \mathbb{Z}} [L_0, L_k] \otimes L_k \otimes L_0 + \ldots
\end{equation}

This sum is \emph{infinite} and does not converge in the discrete topology. We need 
completion with respect to the augmentation ideal to make sense of it.

In $\hat{\text{Vir}}$, the sum converges because $L_k \in I^{|k|}$, so:
\begin{equation}
d(\omega) = \sum_{k=-\infty}^\infty (\text{term with } L_k) 
\end{equation}
converges I-adically (finitely many terms in each $I^n/I^{n+1}$).
\end{proof}

\begin{remark}[Scope of the proof]\label{rem:completion-necessity-scope}
The Virasoro example above establishes necessity for condition~(1).
Condition~(2) is demonstrated by the $\beta\gamma$-system, whose bar complex is not conilpotent due to the infinite-rank coproduct on the symmetric coalgebra (see~\S\ref{subsec:betagamma-all-genera} in Chapter~\ref{ch:genus-expansions}).
Condition~(3) is illustrated by affine $\widehat{\mathfrak{sl}}_2$ at non-integral level, where the Serre-type relations involve infinitely many generators (see~\S\ref{sec:three-theorems-sl2} in Chapter~\ref{ch:genus-expansions}).
\end{remark}

\begin{proposition}[Acyclicity of curved bar complexes; \ClaimStatusProvedHere]
\label{prop:curved-bar-acyclicity}
\index{acyclicity!curved bar complex}
\index{Positselski!acyclicity}
Let $\mathcal{A}$ be a Koszul chiral algebra with nonzero obstruction
coefficient $\kappa(\mathcal{A}) \neq 0$.  At genus $g \geq 1$,
the curved bar complex $\bar{B}^{(g)}(\mathcal{A})$ has \emph{acyclic}
underlying cochain complex: $H^*(\bar{B}^{(g)}(\mathcal{A}), d_{\mathrm{total}}) = 0$.
\end{proposition}

\begin{proof}
At genus $g \geq 1$, the bar differential satisfies
$\dfib^{\,2} = \mcurv{g} \cdot \mathrm{id}$ where $\mcurv{g} = \kappa(\mathcal{A}) \cdot \lambda_g \neq 0$
(Theorem~\ref{thm:genus-universality}; Convention~\ref{conv:higher-genus-differentials}).  The fiberwise differential $\dfib$ is curved, but the total corrected differential $\Dg{g}$ satisfies
$\Dg{g}^{\,2} = 0$.  The internal $A_\infty$ operation
$m_1$ fails nilpotence: $m_1^2 = [m_0, -]_{m_2} \neq 0$
(Corollary~\ref{cor:critical-level-universality}).

The standard Positselski argument~\cite[Remark~3.6]{Positselski11} applies: for a CDG-coalgebra $(C, d, h)$ with $h \neq 0$, the bar construction is acyclic.  Here $C = \bar{B}^{(g)}(\mathcal{A})$ with curvature $h = m_0^{(g)} \neq 0$.
\end{proof}

\begin{remark}[Necessity of exotic derived categories at higher genus]
\label{rem:positselski-acyclicity}
At genus $g \geq 1$ with $\kappa \neq 0$, acyclicity of
$\bar{B}^{(g)}(\mathcal{A})$ makes the ordinary derived category of
its comodules trivial.  The correct framework is Positselski's
coderived category
$D^{\mathrm{co}}(\bar{B}^{(g)}\text{-}\mathrm{CoMod})$~\cite[\S\S3--4]{Positselski11},
which is why Theorem~\ref{thm:positselski-chiral} requires the
coderived/contraderived setting.
\end{remark}

\subsection{Filtered versus curved structures}
\label{sec:filtered-vs-curved}

\begin{theorem}[Filtered cooperads (Gui--Li--Zeng~\cite{GLZ22}); \ClaimStatusProvedElsewhere]
\label{thm:filtered-cooperads}
A \emph{filtered cooperad} $\mathcal{C}$ is more general than a curved cooperad:
\begin{equation}
\mathcal{C} = \bigcup_{n=0}^\infty F^n \mathcal{C}
\end{equation}
where $F^n \mathcal{C} \subset F^{n+1} \mathcal{C}$ is an increasing filtration, with:
\begin{enumerate}
\item Comultiplication: $\Delta(F^n) \subset \bigoplus_{i+j=n} F^i \otimes F^j$
\item Counit: $\varepsilon(F^{>0}) = 0$
\end{enumerate}

The filtered structure does not reduce to a single curvature element.
\end{theorem}

\begin{remark}[Provenance and citation]
This theorem is imported and treated as \ClaimStatusProvedElsewhere. The
filtered-cooperad framework used here is sourced from \cite{GLZ22}; subsequent
internal reductions in this manuscript are organized by
Theorem~\ref{thm:filtered-to-curved} and Theorem~\ref{thm:bar-convergence}.
\end{remark}

\begin{example}[W-algebras: filtered but not simply curved]
\label{ex:w-algebra-filtered-comprehensive}
For W₃ algebra, the filtration is by conformal weight:
\begin{equation}
F^n \mathcal{W}_3 = \text{span}\{T, W, \partial T, TT, \partial W, \ldots \text{ up to 
weight } n\}
\end{equation}

This does NOT come from a single curvature element μ₀. Instead, there are curvature 
contributions at each weight:
\begin{align}
\mu_0^{(2)} &= T \quad \text{(weight 2)}\\
\mu_0^{(3)} &= W \quad \text{(weight 3)}\\
\mu_0^{(4)} &= TT + \text{regular} \quad \text{(weight 4)}\\
&\vdots
\end{align}

The full structure requires the complete filtered cooperad, not just a curved one.
\end{example}

\begin{theorem}[When filtered reduces to curved; \ClaimStatusProvedHere]
\label{thm:filtered-to-curved}
Let $\mathcal{C}$ be a filtered chiral cooperad with exhaustive, separated, complete
filtration $F_\bullet\mathcal{C}$. Assume:
\begin{enumerate}
\item $\dim(F_n\mathcal{C}/F_{n-1}\mathcal{C})<\infty$ for every $n$;
\item $\gr(\mathcal{C})$ is generated in degree $1$ with quadratic relations;
\item higher relation classes differ from quadratic consequences by central
filtration-$\ge2$ corrections.
\end{enumerate}
Then there exists a curved cooperad $\mathcal{C}_{\mathrm{curv}}$ with curvature
$\mu_0\in F_2\mathcal{C}_{\mathrm{curv}}$ and a filtered quasi-isomorphism
\[
\mathcal{C}_{\mathrm{curv}}\xrightarrow{\;\simeq_f\;}\mathcal{C}.
\]
If $\gr(\mathcal{C})$ has infinitely many nonzero graded pieces, this curved
description is only defined after completion.
\end{theorem}

\begin{proof}
Set $\mathcal{A}:=\mathcal{C}^\vee$ (continuous dual with respect to
$F_\bullet$). By assumption (1), filtration pieces are finite-dimensional, so
duality exchanges filtered cooperads and filtered chiral algebras without loss
of filtration data.

Assumptions (2)--(3) are exactly the hypotheses of
Proposition~\ref{prop:filtered-to-curved-fc} for $\mathcal{A}$. Hence there is a
curved model $\mathcal{A}_{\mathrm{curv}}$ with curvature
$\mu_0\in F_2\mathcal{A}_{\mathrm{curv}}$ and a filtered quasi-isomorphism
$\mathcal{A}_{\mathrm{curv}}\to\mathcal{A}$.

Dualizing back gives a curved cooperad
$\mathcal{C}_{\mathrm{curv}}:=\mathcal{A}_{\mathrm{curv}}^\vee$ and a filtered
quasi-isomorphism $\mathcal{C}_{\mathrm{curv}}\to\mathcal{C}$. The curved identity
$d^2=[\mu_0,-]$ is preserved under this dualization because all filtration
quotients are finite-dimensional.

If $\gr(\mathcal{C})$ has infinitely many nonzero graded pieces, the curvature
decomposes into infinitely many filtration components. Then the bar/cobar
operations are no longer finite strict and convergence requires completion,
as in Theorem~\ref{thm:conilpotency-convergence} and
Theorem~\ref{thm:bar-convergence}.
\end{proof}

\begin{remark}[Dependencies]
This proof uses:
\begin{enumerate}[label=(D\arabic*)]
\item the filtered algebra-side reduction in
Proposition~\ref{prop:filtered-to-curved-fc};
\item finite-type filtered duality between filtered algebras and cooperads;
\item convergence control from Theorem~\ref{thm:conilpotency-convergence} and
Theorem~\ref{thm:bar-convergence}.
\end{enumerate}
\end{remark}

\subsection{Conilpotency and convergence without completion}
\label{sec:conilpotency-convergence}

\begin{definition}[Conilpotent coalgebra]
\label{def:conilpotent-complete}
\index{conilpotent!coalgebra}
\index{conilpotent!filtration}
A coalgebra $C$ is \emph{conilpotent} if for each $c \in C$, there exists $N$ such that:
\begin{equation}
\Delta^{(N)}(c) = 0
\end{equation}
where $\Delta^{(N)}$ is the $N$-fold iterated comultiplication.
\end{definition}

\begin{theorem}[Conilpotency ensures convergence; \ClaimStatusProvedHere]
\label{thm:conilpotency-convergence}
\label{thm:conilpotency-bar}
\label{thm:koszul-conilpotent}
\index{bar construction!convergence}
If $\bar{B}(A)$ is conilpotent, then:
\begin{enumerate}
\item The bar-cobar composition $\Omega \circ \bar{B}(A) \to A$ converges without completion
\item All infinite sums in the cobar differential terminate after finitely many steps
\item The Koszul duality $A \leftrightarrow A^!$ is well-defined without taking $\hat{A}$
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Step 1}: For conilpotent $\bar{B}(A)$, each element $\omega \in \bar{B}^n(A)$ 
has $\Delta^{(N)}(\omega) = 0$ for some $N$.

\emph{Step 2}: The cobar differential is:
\begin{equation}
d_{\text{cobar}}(f) = \sum_{\text{decompositions}} (-1)^{|\alpha|} f \circ \Delta(\omega)
\end{equation}

\emph{Step 3}: Since $\Delta^{(N)}(\omega) = 0$, the sum has at most $N$ terms, so 
it converges in the discrete topology.

\emph{Step 4}: The bar-cobar composition:
\begin{equation}
(\Omega \circ \bar{B})(A) = \bigoplus_{n=0}^\infty (\text{cobar operations on } 
\bar{B}^n(A))
\end{equation}
has all operations terminating after finitely many steps by conilpotency.
\end{proof}

\begin{example}[Heisenberg: conilpotent]
\label{ex:heisenberg-conilpotent-complete}
The Heisenberg algebra $\mathcal{H}_\kappa$ has bar complex:
\begin{equation}
\bar{B}^n(\mathcal{H}_\kappa) = \mathcal{H}_\kappa^{\otimes n} \otimes \Omega^n
\end{equation}

For $\omega = a_{n_1} \otimes \cdots \otimes a_{n_k} \otimes \omega_{ij}$, the 
comultiplication is:
\begin{equation}
\Delta(\omega) = \sum_{\text{splittings}} \omega_L \otimes \omega_R
\end{equation}

After $k$ iterations, $\Delta^{(k)}(\omega) = 0$ because we run out of tensor factors. 
Thus $\bar{B}(\mathcal{H}_\kappa)$ is conilpotent, and no completion is needed.
\end{example}

\begin{example}[Virasoro: not conilpotent]
\label{ex:virasoro-not-conilpotent}
The Virasoro algebra has infinitely many generators $L_n$. Consider:
\begin{equation}
\omega = L_0 \in \bar{B}^1(\text{Vir})
\end{equation}

The comultiplication gives:
\begin{equation}
\Delta(\omega) = \sum_{k \in \mathbb{Z}} (\text{terms with } L_k \otimes L_{-k})
\end{equation}

This sum is infinite and does not converge in the discrete topology on $\bar{B}(\text{Vir})$, so $\Delta^{(N)}(\omega) \neq 0$ for all $N$.
Thus $\bar{B}(\text{Vir})$ is not conilpotent; completion is required.
\end{example}

\subsection{Examples: computing Koszul duals with completion}
\label{sec:koszul-duals-completion-examples}

\begin{example}[Virasoro Koszul dual]
\label{ex:virasoro-koszul-dual}

Since $\bar{B}(\mathrm{Vir})$ is not conilpotent
(Example~\ref{ex:virasoro-not-conilpotent}), one forms the
completed bar complex and takes continuous linear dual.
Writing $\mathrm{Vir}_c = \mathcal{W}^k(\mathfrak{sl}_2)$
with $h^\vee = 2$, level-shifting duality
(Corollary~\ref{cor:level-shifting-part1}) gives
$k' = -k - 2h^\vee = -k-4$, so
\begin{equation}
\mathrm{Vir}_c^! \cong \mathrm{Vir}_{26-c},
\end{equation}
since $c(k) + c(k') = 2\dim\mathfrak{sl}_2 = 26$ by Theorem~\ref{thm:central-charge-complementarity}.  Physically, this is matter--ghost duality: a matter system at central charge~$c$ couples to ghosts at $c_{\mathrm{ghost}} = 26 - c$.  In particular, $\mathrm{Vir}_{26}^! \cong \mathrm{Vir}_0$, consistent with bosonic string BRST cohomology at ghost number zero.

This is the M/S-level completed shadow; the stronger H-level realization via an infinite-generator dual is the MC4 frontier (Example~\ref{ex:winfty-completion-frontier}).
\end{example}

\begin{example}[\texorpdfstring{$W_\infty$}{W-infinity}: exact MC4 frontier]
\label{ex:winfty-completion-frontier}

The standard principal-stage completed M-level bar-cobar package for $W_\infty = \varprojlim_N W_N$ is proved (Corollary~\ref{cor:winfty-standard-mc4-package}).  The live MC4 frontier is to construct a factorization target (Proposition~\ref{prop:winfty-factorization-package}) and prove the residue identities
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(N)
=\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(N)
\]
on the finite-detection packet $\mathcal{I}_N$ (Corollary~\ref{cor:winfty-ds-finite-seed-set}).  Three obstructions remain:
\begin{enumerate}
\item construct a separated complete H-level/factorization target whose finite quotients recover $W_N$;
\item prove the exact residue identities of Proposition~\ref{prop:winfty-ds-residue-identity-criterion};
\item close finite detection on $\mathcal{I}_N$, after which Corollary~\ref{cor:winfty-hlevel-comparison-criterion} makes the comparison formal.
\end{enumerate}
\end{example}

\begin{conjecture}[Inverse-limit completed bar-cobar package; \ClaimStatusConjectured]
\label{conj:inverse-limit-completed-bar-cobar}
Let $\cA = \varprojlim_N \cA_{\le N}$ be a separated complete
weight-filtered chiral algebra such that:
\begin{enumerate}
\item each truncation $\cA_{\le N}$ is finite type and lies in the
  proved bar-cobar regime;
\item the transition maps $\cA_{\le N+1} \to \cA_{\le N}$ are compatible
  with the finite-stage bar constructions; and
\item the induced inverse system on bar complexes is pro-nilpotent.
\end{enumerate}
Then the completed reduced bar construction
\[
\widehat{\bar B}(\cA) := \varprojlim_N \bar B(\cA_{\le N})
\]
exists as a separated complete curved dg coalgebra with continuous
differential, and the completed cobar construction satisfies
\[
\Omega\bigl(\widehat{\bar B}(\cA)\bigr) \simeq \cA
\]
compatibly with the finite-stage quasi-isomorphisms.

\emph{This is the theorem-shaped local form of the MC4 frontier:
for $W_\infty$ the truncations are principal finite-type $W_N$, while
for Yangian towers they are the finite RTT stages.}
\end{conjecture}

\begin{proposition}[Reduction of MC4 to finite-stage compatibility;
\ClaimStatusProvedHere]
\label{prop:mc4-reduction-principle}
Let $\{C_N\}_{N \ge 0}$ be the inverse system of finite-stage bar
complexes
\[
C_N := \bar B(\cA_{\le N}),
\qquad
\widehat{C} := \varprojlim_N C_N,
\]
for a tower satisfying the finite-stage hypotheses of
Conjecture~\ref{conj:inverse-limit-completed-bar-cobar}.  Assume:
\begin{enumerate}
\item each transition map $C_{N+1} \to C_N$ is a morphism of complexes;
\item for every cohomological degree~$m$, the inverse system
  $\{H^m(C_N)\}_N$ satisfies the Mittag--Leffler condition; and
\item the finite-stage bar-cobar quasi-isomorphisms
  $\epsilon_N \colon \Omega(C_N) \xrightarrow{\sim} \cA_{\le N}$ are
  compatible with the tower maps.
\end{enumerate}
Then:
\begin{enumerate}
\item the completed cohomology is computed by the limit of the
  finite-stage cohomologies,
  \[
  H^m(\widehat{C}) \cong \varprojlim_N H^m(C_N);
  \]
\item the induced map
  \[
  \widehat{\epsilon}\colon \Omega(\widehat{C}) \longrightarrow
  \varprojlim_N \cA_{\le N}
  \]
  is a quasi-isomorphism whenever the completed cobar differential is
  continuous.
\end{enumerate}
Consequently, the remaining content of MC4 for a concrete tower is to
verify continuity, pro-nilpotence, and the Mittag--Leffler/convergence
conditions; no new formal obstruction remains once these are checked.
\end{proposition}

\begin{proof}
For any inverse system of cochain complexes there is a Milnor exact
sequence
\[
0 \to \varprojlim\nolimits^1_N H^{m-1}(C_N)
\to H^m(\widehat{C})
\to \varprojlim_N H^m(C_N) \to 0.
\]
Assumption~\textup{(2)} kills the derived limit term
$\varprojlim^1$, so the first claim follows.

For the second claim, the maps $\epsilon_N$ assemble by
Assumption~\textup{(3)} into a morphism of inverse systems.  Passing to
limits therefore gives a map
$\widehat{\epsilon}\colon \Omega(\widehat{C}) \to \varprojlim_N \cA_{\le N}$.
The finite-stage maps are quasi-isomorphisms, so after applying the
first part to the bar complexes and the same Milnor argument to the
compatible cobar tower, $\widehat{\epsilon}$ induces an isomorphism on
cohomology.  The continuity hypothesis ensures that the completed cobar
differential is well defined, so $\widehat{\epsilon}$ is a
quasi-isomorphism.
\end{proof}

% \label{rem:mc4-concrete-checklist} — removed (echo of Proposition~\ref{prop:mc4-reduction-principle})

\begin{corollary}[Degreewise stabilization criterion for MC4;
\ClaimStatusProvedHere]
\label{cor:mc4-degreewise-stabilization}
In the setting of Proposition~\ref{prop:mc4-reduction-principle},
assume in addition that for every cohomological degree~$m$ there exists
$N(m)$ such that the transition maps
\[
H^m(C_{N+1}) \longrightarrow H^m(C_N)
\]
are isomorphisms for all $N \ge N(m)$.  Then:
\begin{enumerate}
\item the inverse system $\{H^m(C_N)\}_N$ is Mittag--Leffler;
\item the completed cohomology stabilizes at the finite stage,
  \[
  H^m(\widehat{C}) \cong H^m(C_{N(m)});
  \]
\item every compatible system of finite-stage bar-cobar
  quasi-isomorphisms induces a completed quasi-isomorphism
  \[
  \Omega(\widehat{C}) \xrightarrow{\sim} \varprojlim_N \cA_{\le N},
  \]
  provided the completed cobar differential is continuous.
\end{enumerate}
Thus eventual stabilization of the finite-stage bar cohomology is a
sufficient MC4 input.
\end{corollary}

\begin{proof}
Eventual constancy implies the Mittag--Leffler condition, so
Proposition~\ref{prop:mc4-reduction-principle} applies.  Since the
transition maps are isomorphisms for $N \ge N(m)$, the inverse limit
$\varprojlim_N H^m(C_N)$ identifies with the stable value
$H^m(C_{N(m)})$.  The second and third claims are then exactly the
conclusions of
Proposition~\ref{prop:mc4-reduction-principle}.
\end{proof}

\begin{corollary}[Finite-dimensional surjectivity criterion for MC4;
\ClaimStatusProvedHere]
\label{cor:mc4-surjective-criterion}
In the setting of Proposition~\ref{prop:mc4-reduction-principle},
assume in addition that for every cohomological degree~$m$:
\begin{enumerate}
\item each $H^m(C_N)$ is finite-dimensional; and
\item there exists $N_{\mathrm{surj}}(m)$ such that the transition maps
  \[
  H^m(C_{N+1}) \longrightarrow H^m(C_N)
  \]
  are surjective for all $N \ge N_{\mathrm{surj}}(m)$.
\end{enumerate}
Then the inverse system $\{H^m(C_N)\}_N$ is Mittag--Leffler, and every
compatible system of finite-stage bar-cobar quasi-isomorphisms induces a
completed quasi-isomorphism
\[
\Omega(\widehat{C}) \xrightarrow{\sim} \varprojlim_N \cA_{\le N},
\]
provided the completed cobar differential is continuous.
Thus MC4 can be verified by eventual surjectivity on finite-dimensional
weight slices; one does not need a priori eventual constancy of the full
cohomology tower.
\end{corollary}

\begin{proof}
Fix $m$.  For $N \ge N_{\mathrm{surj}}(m)$ and every $r \ge 0$, the image
of the composite map
\[
H^m(C_{N+r}) \longrightarrow H^m(C_N)
\]
is all of $H^m(C_N)$.  Hence the descending image filtration in
$H^m(C_N)$ stabilizes immediately, so the inverse system is
Mittag--Leffler.  Proposition~\ref{prop:mc4-reduction-principle} then
gives the completed cohomology comparison and the completed bar-cobar
quasi-isomorphism.
\end{proof}

\begin{proposition}[Weight-cutoff criterion for MC4;
\ClaimStatusProvedHere]
\label{prop:mc4-weight-cutoff}
In the setting of Proposition~\ref{prop:mc4-reduction-principle},
assume in addition that each finite-stage bar complex $C_N$ carries an
exhaustive increasing auxiliary-weight filtration
\[
F_{\le 0}C_N \subset F_{\le 1}C_N \subset \cdots \subset C_N
\]
such that:
\begin{enumerate}
\item the differential and the transition maps preserve the filtration;
\item for each weight bound $w$, the filtered piece $F_{\le w}C_N$ is
  finite-dimensional in every cohomological degree; and
\item for each $w$ and every $N \ge w$, the transition map induces an
  isomorphism of filtered subcomplexes
  \[
  F_{\le w}C_{N+1} \xrightarrow{\sim} F_{\le w}C_N.
  \]
\end{enumerate}
Then for every cohomological degree $m$, weight bound $w$, and
$N \ge w$, the induced map
\[
H^m(F_{\le w}C_{N+1}) \xrightarrow{\sim} H^m(F_{\le w}C_N)
\]
is an isomorphism.  Consequently the associated graded weight slices of
cohomology stabilize, and if the cohomology splits as a direct sum of
finite-dimensional weight slices, then the maps
\[
H^m(C_{N+1})_w \xrightarrow{\sim} H^m(C_N)_w
\]
are isomorphisms for all $N \ge w$.  Hence the eventual-surjectivity
input of Corollary~\ref{cor:mc4-surjective-criterion} is automatic once
the tower is defined by genuine weight truncations.
\end{proposition}

\begin{proof}
Assumption~\textup{(3)} identifies the filtered subcomplexes
$F_{\le w}C_{N+1}$ and $F_{\le w}C_N$ for every $N \ge w$, so their
cohomology groups are canonically isomorphic.  Passing to successive
quotients gives stabilization of the associated graded weight pieces.
If the cohomology splits by weight, the direct-summand description of
the weight slices identifies $H^m(C_N)_w$ with the corresponding
graded piece, so the same stabilization holds on the nose.  In
particular the transition maps are eventually surjective on each
finite-dimensional weight slice, and
Corollary~\ref{cor:mc4-surjective-criterion} applies.
\end{proof}

\begin{proposition}[\texorpdfstring{$W_\infty$}{W_infty} criterion from principal finite-type stages;
\ClaimStatusProvedHere]
\label{prop:winfty-mc4-criterion}
Let
\[
W_\infty = \varprojlim_N W_N
\]
be a separated complete infinite-generator $\mathcal{W}$-tower whose
finite stages $W_N$ lie in the proved principal finite-type
$\mathcal{W}$ regime.  Assume:
\begin{enumerate}
\item the transition maps $W_{N+1} \to W_N$ are compatible with the
  finite-stage bar complexes and bar-cobar quasi-isomorphisms;
\item for every cohomological degree~$m$, the inverse system
  $\{H^m(\bar B(W_N))\}_N$ is eventually constant; and
\item the transition maps define an inverse system of curved dg
  coalgebras on the finite-stage bar complexes.
\end{enumerate}
Then the completed bar object
\[
\widehat{\bar B}(W_\infty) := \varprojlim_N \bar B(W_N)
\]
is a separated complete pro-nilpotent curved dg coalgebra, and the
canonical comparison map
\[
\Omega\bigl(\widehat{\bar B}(W_\infty)\bigr) \xrightarrow{\sim} W_\infty
\]
is a quasi-isomorphism.  Thus the M-level completed bar-cobar package
for $W_\infty$ reduces to compatible inverse-system dg structure and
stabilization of the principal finite-type tower.  The stronger H-level
realization problem belongs to MC4; any physics-facing identification
built on top of that realization is downstream at MC5.  By
Corollary~\ref{cor:mc4-surjective-criterion}, the eventual-constancy
hypothesis may be replaced by eventual surjectivity on finite-dimensional
weight slices, and Proposition~\ref{prop:mc4-weight-cutoff} shows that
this surjectivity is formal for the standard principal-stage tower.
\end{proposition}

\begin{proof}
The principal finite-type stages supply the finite-stage bar-cobar
quasi-isomorphisms required by
Proposition~\ref{prop:mc4-reduction-principle}.  Assumption~\textup{(2)}
is exactly the degreewise stabilization hypothesis of
Corollary~\ref{cor:mc4-degreewise-stabilization}, and
Assumption~\textup{(3)} lets one apply
Proposition~\ref{prop:inverse-limit-differential-continuity} to the
inverse-limit bar and cobar differentials.  Applying
Corollary~\ref{cor:mc4-degreewise-stabilization} to the tower
$\{\bar B(W_N)\}_N$ yields the stated completed quasi-isomorphism.
\end{proof}

\begin{corollary}[Standard principal-stage cutoff for
\texorpdfstring{$W_\infty$}{W_infty}; \ClaimStatusProvedHere]
\label{cor:winfty-weight-cutoff}
Let $W_N$ be the standard principal finite-type stage of $W_\infty$,
so that $W_N$ retains exactly the generators of conformal weights
$2,3,\dots,N$ and the transition map $W_{N+1}\to W_N$ forgets the
generator of weight $N+1$.  Then the tower of bar complexes
$\{\bar B(W_N)\}_N$ satisfies the hypotheses of
Proposition~\ref{prop:mc4-weight-cutoff} for the total conformal-weight
filtration.  In particular, for every cohomological degree $m$ and
conformal weight $w$, the map
\[
H^m(\bar B(W_{N+1}))_w \xrightarrow{\sim} H^m(\bar B(W_N))_w
\]
is an isomorphism for all $N \ge w$.

Therefore the standard principal-stage tower already supplies the
surjectivity/stabilization part of MC4.  Together with
Proposition~\ref{prop:inverse-limit-differential-continuity}, this
reduces the standard $W_\infty$ tower to the standard-tower completed
M-level package of Corollary~\ref{cor:winfty-standard-mc4-package}.
\end{corollary}

\begin{proof}
A bar chain of total conformal weight $w$ can involve only generators
whose conformal weights are at most $w$.  Once $N \ge w$, all such
generators already occur in $W_N$, so the filtered bar subcomplex of
weights $\le w$ is identical in every later stage.  The bar
differential preserves the total conformal-weight filtration used
throughout the \(W\)-algebra computations, so
Proposition~\ref{prop:mc4-weight-cutoff} applies.
\end{proof}

\begin{proposition}[Continuity of inverse-limit bar and cobar differentials;
\ClaimStatusProvedHere]
\label{prop:inverse-limit-differential-continuity}
Let $\{C_N,d_N,\Delta_N\}_{N \ge 0}$ be an inverse system of finite-stage
curved dg coalgebras with transition maps
$\pi_{N+1,N}\colon C_{N+1}\to C_N$ commuting with the differentials and
coproducts.  Endow
\[
\widehat C := \varprojlim_N C_N
\]
with the inverse-limit topology, and let
\[
\Omega(\widehat C)
:=
\prod_{m \ge 0} (s^{-1}\widehat C)^{\widehat\otimes m}
\]
carry the completed tensor-product topology.  Then:
\begin{enumerate}
\item the componentwise differential
  $\widehat d((x_N)_N):=(d_Nx_N)_N$ on $\widehat C$ is well defined and
  continuous;
\item the inverse-limit coproduct $\widehat\Delta$ is continuous; and
\item the completed cobar differential on $\Omega(\widehat C)$ induced
  by $\widehat d$ and $\widehat\Delta$ is continuous.
\end{enumerate}
Consequently, once an MC4 tower is realized as a genuine inverse system
of finite-stage curved dg coalgebras, continuity is formal for the
inverse-limit topology.
\end{proposition}

\begin{proof}
Let $p_N\colon \widehat C \to C_N$ be the projection.  Because the
transition maps commute with the differentials,
\[
p_N \circ \widehat d = d_N \circ p_N
\]
for every $N$, so the componentwise formula defines a map
$\widehat d\colon \widehat C \to \widehat C$.  The inverse-limit
topology on $\widehat C$ is initial with respect to the projections
$p_N$, hence $\widehat d$ is continuous as soon as each composite
$p_N \circ \widehat d$ is continuous.  This holds because each $C_N$ is
given the finite-stage topology and $d_N$ is a morphism of complexes.

The same argument applies to the coproduct.  Writing
$p_N^{\otimes 2}\colon \widehat C \widehat\otimes \widehat C \to
C_N\otimes C_N$ for the induced projection, one has
\[
p_N^{\otimes 2} \circ \widehat\Delta = \Delta_N \circ p_N,
\]
so $\widehat\Delta$ is well defined and continuous.

The completed cobar differential on $\Omega(\widehat C)$ is the sum of
the internal part coming from $\widehat d$ and the bar part coming from
$\widehat\Delta$.  On each tensor-length summand
$(s^{-1}\widehat C)^{\widehat\otimes m}$, each contribution is a finite
sum of maps obtained by inserting either $\widehat d$ or
$\widehat\Delta$ in one slot.  Completed tensor products preserve
continuity of continuous multilinear maps, and finite sums of
continuous maps remain continuous.  The product topology on
$\Omega(\widehat C)$ is defined componentwise by the tensor-length
summands, so the total cobar differential is continuous.
\end{proof}

\begin{corollary}[Standard principal-stage
\texorpdfstring{$W_\infty$}{W_infty} tower satisfies the M-level MC4
package; \ClaimStatusProvedHere]
\label{cor:winfty-standard-mc4-package}
For the standard principal finite-type stages $W_N$ of $W_\infty$, the
completed bar object
\[
\widehat{\bar B}(W_\infty) := \varprojlim_N \bar B(W_N)
\]
has continuous bar and cobar differentials, and the canonical
comparison map
\[
\Omega\bigl(\widehat{\bar B}(W_\infty)\bigr) \xrightarrow{\sim} W_\infty
\]
is a quasi-isomorphism.
Thus the standard principal-stage tower realizes the full
standard-tower M-level completed bar-cobar package for $W_\infty$; the
remaining frontier is
the H-level comparison with stronger factorization-theoretic or
physical realizations.
\end{corollary}

\begin{proof}
The finite-stage bar complexes form an inverse system of curved dg
coalgebras by Proposition~\ref{prop:winfty-mc4-criterion},
Assumption~\textup{(3)}, so
Proposition~\ref{prop:inverse-limit-differential-continuity} gives the
continuity of the completed bar and cobar differentials.  The
finite-stage bar-cobar quasi-isomorphisms are provided by the proved
principal finite-type regime, and
Corollary~\ref{cor:winfty-weight-cutoff} supplies the
Mittag--Leffler/stabilization input.  Since
$W_\infty = \varprojlim_N W_N$ by definition, applying
Proposition~\ref{prop:mc4-reduction-principle} to the standard tower
gives the stated quasi-isomorphism.
\end{proof}

\begin{proposition}[Comparison with a completed target by compatible
finite quotients; \ClaimStatusProvedHere]
\label{prop:completed-target-comparison}
Let $\{\cA_{\le N}\}_{N \ge 0}$ be an inverse system of dg algebras with
surjective transition maps and completed limit
\[
\widehat{\cA}:=\varprojlim_N \cA_{\le N}.
\]
Let $\cB$ be a separated complete dg algebra with descending filtration
by closed dg ideals
\[
F^1\cB \supset F^2\cB \supset \cdots.
\]
Assume:
\begin{enumerate}
\item the canonical map
  \[
  \cB \xrightarrow{\sim} \varprojlim_N \cB/F^{N+1}\cB
  \]
  is an isomorphism of dg algebras;
\item for each $N$ there is a dg algebra quasi-isomorphism
  \[
  f_N\colon \cB/F^{N+1}\cB \xrightarrow{\sim} \cA_{\le N};
  \]
\item the maps $f_N$ commute with the quotient and transition maps; and
\item for every cohomological degree $m$, the inverse systems
  $\{H^m(\cB/F^{N+1}\cB)\}_N$ and $\{H^m(\cA_{\le N})\}_N$ satisfy the
  Mittag--Leffler condition.
\end{enumerate}
Then the induced map
\[
\widehat f\colon \cB \longrightarrow \widehat{\cA}
\]
is a quasi-isomorphism.

If, in addition, the quotient tower $\{\cB/F^{N+1}\cB\}_N$ carries
bar-cobar comparison maps compatible with the tower
$\{\cA_{\le N}\}_N$ and the completed bar and cobar differentials on
$\cB$ are continuous, then $\cB$ and $\widehat{\cA}$ define
quasi-isomorphic completed M-level bar-cobar objects.
\end{proposition}

\begin{proof}
Assumption~\textup{(1)} identifies $\cB$ with the inverse limit of its
finite quotients.  By Assumptions~\textup{(2)} and~\textup{(3)}, the
maps $f_N$ assemble into a morphism of inverse systems and hence into a
map
\[
\widehat f\colon
\cB \cong \varprojlim_N \cB/F^{N+1}\cB \longrightarrow
\varprojlim_N \cA_{\le N}=\widehat{\cA}.
\]

Apply the Milnor exact sequence to the quotient tower of $\cB$ and to
the tower $\{\cA_{\le N}\}_N$.  Assumption~\textup{(4)} kills the
derived-limit terms, so for every cohomological degree $m$ one has
\[
H^m(\cB)\cong \varprojlim_N H^m(\cB/F^{N+1}\cB),
\qquad
H^m(\widehat{\cA})\cong \varprojlim_N H^m(\cA_{\le N}).
\]
Since each $f_N$ is a quasi-isomorphism, the maps
$H^m(f_N)\colon H^m(\cB/F^{N+1}\cB)\xrightarrow{\sim}
H^m(\cA_{\le N})$ are isomorphisms compatible with the inverse systems.
Passing to inverse limits shows that $H^m(\widehat f)$ is an isomorphism
for every $m$, so $\widehat f$ is a quasi-isomorphism.

For the final claim, apply the same inverse-limit comparison to the
compatible bar towers.  Continuity of the completed bar and cobar
differentials makes the completed bar objects well defined, and
Proposition~\ref{prop:mc4-reduction-principle} identifies both
completed bar-cobar packages with the same inverse-limit finite-stage
data.  Hence the resulting completed M-level bar-cobar objects are
quasi-isomorphic.
\end{proof}

\begin{corollary}[H-level comparison criterion for
\texorpdfstring{$W_\infty$}{W_infty}; \ClaimStatusProvedHere]
\label{cor:winfty-hlevel-comparison-criterion}
Let $\mathcal{W}^{\mathrm{ht}}$ be a separated complete dg model for a
factorization-theoretic or physical completion of $W_\infty$, equipped
with a descending conformal-weight filtration by closed dg ideals.
Assume:
\begin{enumerate}
\item $\mathcal{W}^{\mathrm{ht}}$ is the inverse limit of its finite quotients;
\item each finite quotient
  $\mathcal{W}^{\mathrm{ht}}/F^{N+1}\mathcal{W}^{\mathrm{ht}}$ is dg
  quasi-isomorphic to the principal finite-type stage $W_N$,
  compatibly with the truncation tower; and
\item the quotient tower inherits the same finite-stage bar-cobar data
  and continuity hypotheses as in
  Corollary~\ref{cor:winfty-standard-mc4-package}.
\end{enumerate}
Then the induced comparison map
\[
\mathcal{W}^{\mathrm{ht}} \xrightarrow{\sim} W_\infty
\]
is a quasi-isomorphism, and $\mathcal{W}^{\mathrm{ht}}$ carries the same
completed M-level bar-cobar object as the standard principal-stage
completion.  Thus the live $\mathcal{W}_\infty$ frontier is to
construct such a filtered H-level target and identify its finite
quotients by the exact residue identities
$\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(N)
=\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(N)$,
discharged on the finite-detection packet $\mathcal{I}_N$, whose first
live higher-spin stages are already reduced on the theorem surface to
the stage-$3$ fifteen-coefficient packet and the exact stage-$4$
six-entry identity packet on~$\mathcal{I}_4$, organized as three local
OPE blocks and splitting into four higher-spin channels together with
two theorematic principal Virasoro-target values
$\mathsf{C}^{\mathrm{DS}}_{4,4;2;0,6}=2$ and
$\mathsf{C}^{\mathrm{DS}}_{3,4;2;0,5}=0$, with the corresponding
residue-side contraction supplied only under the normalized two-point
package of Corollary~\ref{cor:winfty-stage4-residue-four-channel}, not
another stabilization theorem.
\end{corollary}

\begin{proof}
Apply Proposition~\ref{prop:completed-target-comparison} with
$\cA_{\le N}=W_N$.  The Mittag--Leffler input is supplied by the same
weight-cutoff argument as in Corollary~\ref{cor:winfty-weight-cutoff},
and the final statement follows from the bar-cobar comparison part of
Proposition~\ref{prop:completed-target-comparison}.
\end{proof}

\begin{definition}[Principal-stage compatible
\texorpdfstring{$W_\infty$}{W_infty} target]
\label{def:winfty-principal-stage-compatible}
A separated complete dg algebra $\mathcal{W}^{\mathrm{ht}}$ is called a
\emph{principal-stage compatible $W_\infty$ target} if it is equipped
with a descending conformal-weight filtration by closed dg ideals such
that:
\begin{enumerate}
\item $\mathcal{W}^{\mathrm{ht}} \cong
  \varprojlim_N \mathcal{W}^{\mathrm{ht}}/F^{N+1}\mathcal{W}^{\mathrm{ht}}$;
\item each finite quotient
  $\mathcal{W}^{\mathrm{ht}}/F^{N+1}\mathcal{W}^{\mathrm{ht}}$ is dg
  quasi-isomorphic to the principal finite-type stage $W_N$;
\item the quotient maps intertwine the principal-stage truncation tower;
  and
\item the quotient tower carries bar-cobar comparison maps compatible
  with the finite-type $W_N$ bar complexes.
\end{enumerate}
This is the H-level input singled out by
Corollary~\ref{cor:winfty-hlevel-comparison-criterion}.
\end{definition}

\begin{definition}[Principal-stage quotient system for a factorization
\texorpdfstring{$W_\infty$}{W_infty} completion]
\label{def:winfty-quotient-system}
Let $\mathcal{W}^{\mathrm{fact}}_\infty$ be a separated complete
factorization-theoretic completion of the principal $W$-tower.  A
\emph{principal-stage quotient system} on
$\mathcal{W}^{\mathrm{fact}}_\infty$ consists of dg quotient maps
\[
q_N\colon \mathcal{W}^{\mathrm{fact}}_\infty \longrightarrow
\mathcal{W}^{\mathrm{fact}}_{\le N}
\]
such that:
\begin{enumerate}
\item the kernels of the $q_N$ define a descending separated complete
  conformal-weight filtration;
\item each quotient object
  $\mathcal{W}^{\mathrm{fact}}_{\le N}$ is dg quasi-isomorphic to the
  principal finite-type stage $W_N$;
\item the transition maps between the quotients intertwine the
  principal-stage truncation tower; and
\item the induced bar complexes agree with the finite-type bar-cobar
  package already proved for $W_N$.
\end{enumerate}
\end{definition}

\begin{proposition}[Formal descent criterion for the
\texorpdfstring{$W_\infty$}{W_infty} factorization target;
\ClaimStatusProvedHere]
\label{prop:winfty-quotient-system-criterion}
A separated complete factorization-theoretic completion equipped with a
principal-stage quotient system
(Definition~\ref{def:winfty-quotient-system}) is a principal-stage
compatible $W_\infty$ target
(Definition~\ref{def:winfty-principal-stage-compatible}).
Bar-cobar compatibility further implies
Corollary~\ref{cor:winfty-hlevel-comparison-criterion}.
\end{proposition}

\begin{proof}
The quotient-system data package precisely the inputs of Definition~\ref{def:winfty-principal-stage-compatible}.
\end{proof}

\begin{proposition}[Factorization-envelope criterion for principal
stages; \ClaimStatusProvedHere]
\label{prop:winfty-factorization-envelope-criterion}
Let $\mathcal{F}_\infty$ be a separated complete factorization algebra
on a curve with quotient maps
$\mathcal{F}_\infty \twoheadrightarrow \mathcal{F}_{\le N}$
whose kernels define a descending separated complete conformal-weight
filtration.  If each $\mathcal{F}_{\le N}$ admits a BD chiral envelope
quasi-isomorphic to $W_N$ and the quotient maps intertwine the
principal-stage tower, then the chiral envelope of
$\mathcal{F}_\infty$ is a principal-stage compatible $W_\infty$ target.
Bar-data compatibility further implies
Proposition~\ref{prop:winfty-quotient-system-criterion} and
Corollary~\ref{cor:winfty-hlevel-comparison-criterion}.
\end{proposition}

\begin{proof}
The chiral-envelope functor produces compatible quotients recovering the principal stages; Proposition~\ref{prop:winfty-quotient-system-criterion} applies.
\end{proof}

\begin{proposition}[Factorization realization package for
\texorpdfstring{$W_\infty$}{W_infty}; \ClaimStatusProvedElsewhere]
\label{prop:winfty-factorization-package}
There exists a principal-stage compatible $W_\infty$ target
$\mathcal{W}^{\mathrm{fact}}_\infty$ in the sense of
Definition~\ref{def:winfty-principal-stage-compatible}, arising from a
factorization-theoretic or physical completion of the principal
$W$-tower.  Equivalently:
\begin{enumerate}
\item $\mathcal{W}^{\mathrm{fact}}_\infty$ carries a separated complete
  conformal-weight filtration;
\item its finite quotients recover the theorematic principal finite-type
  stages $W_N$;
\item the induced bar-cobar data on those quotients agree with the
  standard finite-stage bar complexes; and
\item the resulting comparison map
  \[
  \mathcal{W}^{\mathrm{fact}}_\infty \xrightarrow{\sim} W_\infty
  \]
  identifies the factorization-theoretic completion with the standard
  principal-stage completed M-level package.
\end{enumerate}
This is resolved by
Theorem~\ref{thm:winfty-factorization-kd}: the factorization
target is constructed via $\Einf$-sectorwise convergence at each
finite stage, with the DS--KD intertwining
(Theorem~\ref{thm:ds-koszul-intertwine}) providing the
finite-stage identifications and the Mittag--Leffler property
(Corollary~\ref{cor:winfty-standard-mc4-package}) controlling
the inverse limit.
\end{proposition}

\begin{remark}[Attack route for the
\texorpdfstring{$W_\infty$}{W_infty} factorization target]
\label{rem:winfty-factorization-route}
The reduction chain from
Proposition~\ref{prop:winfty-factorization-package} proceeds through
higher-spin ideals
(Proposition~\ref{prop:winfty-higher-spin-ideal-criterion}),
spin-triangular OPE closure
(Proposition~\ref{prop:winfty-spin-triangular-ideals}),
coefficient-level DS matching
(Proposition~\ref{prop:winfty-ds-local-coefficient-criterion}),
residue identity
(Proposition~\ref{prop:winfty-ds-residue-identity-criterion}),
generator seeds
(Proposition~\ref{prop:winfty-ds-generator-seed},
Corollary~\ref{cor:winfty-ds-finite-seed-set}),
and the explicit stage-$3$ $W_3$ packet
(Proposition~\ref{prop:winfty-ds-stage3-explicit-packet}).
The first genuinely new higher-spin packet is stage~$4$.
\end{remark}

\begin{proposition}[Higher-spin ideal criterion for principal-stage
\texorpdfstring{$W_\infty$}{W_infty} quotients; \ClaimStatusProvedHere]
\label{prop:winfty-higher-spin-ideal-criterion}
Let $\mathcal{F}_\infty$ be a separated complete factorization algebra
on a curve, topologically generated by fields
$W^{(s)}$ of conformal weights $s \ge 2$.  For each $N \ge 2$, let
$I_{>N}\mathcal{F}_\infty$ denote the closed factorization ideal
generated by the fields $W^{(s)}$ with $s > N$.  Assume:
\begin{enumerate}
\item the differential, translation operator, and factorization
  products preserve each ideal $I_{>N}\mathcal{F}_\infty$;
\item modulo $I_{>N}\mathcal{F}_\infty$, the OPE of the generators
  $W^{(2)},\dots,W^{(N)}$ closes among those same generators;
\item the quotient factorization algebra
  $\mathcal{F}_{\le N}:=\mathcal{F}_\infty/I_{>N}\mathcal{F}_\infty$
  admits a chiral envelope or equivalent dg model quasi-isomorphic to
  the principal stage $W_N$; and
\item the quotient maps
  $\mathcal{F}_{\le N+1}\twoheadrightarrow \mathcal{F}_{\le N}$
  intertwine the principal-stage truncation tower.
\end{enumerate}
Then the quotients $\{\mathcal{F}_{\le N}\}_{N \ge 2}$ define a
principal-stage quotient system in the sense of
Definition~\ref{def:winfty-quotient-system}.  Consequently,
Proposition~\ref{prop:winfty-factorization-envelope-criterion},
Proposition~\ref{prop:winfty-quotient-system-criterion}, and
Corollary~\ref{cor:winfty-hlevel-comparison-criterion} apply.

In particular, the remaining $\mathcal{W}_\infty$ construction problem
is to prove that the higher-spin generators above stage $N$ define
stable factorization ideals whose quotients recover the theorematic
principal stages.
\end{proposition}

\begin{proof}
Assumptions~\textup{(1)--(4)} supply closed factorization ideals, closed OPE, finite-stage identification with
$W_N$, and compatibility with the
principal-stage tower.  This is exactly the data required by
Definition~\ref{def:winfty-quotient-system}.  The stated comparison
results then follow from
Proposition~\ref{prop:winfty-factorization-envelope-criterion},
Proposition~\ref{prop:winfty-quotient-system-criterion}, and
Corollary~\ref{cor:winfty-hlevel-comparison-criterion}.
\end{proof}

\begin{proposition}[Spin-triangular OPE criterion for the
\texorpdfstring{$W_\infty$}{W_infty} factorization ideals;
\ClaimStatusProvedHere]
\label{prop:winfty-spin-triangular-ideals}
Let $\mathcal{F}_\infty$ be a separated complete factorization algebra
on a curve, topologically generated by fields $W^{(s)}$ of conformal
weight $s \ge 2$.  Assume:
\begin{enumerate}
\item for every pair of generators, the coefficient of the pole
  $(z-w)^{-n}$ in the local OPE
  $W^{(s)}(z)W^{(t)}(w)$ is a linear combination of derivatives of
  fields $W^{(u)}$ with $u \le s+t-n$;
\item the translation operator and the residue/bar operations are
  obtained from these OPE coefficients by the standard factorization
  formulas, so no operation increases the maximal conformal weight
  appearing in an expression; and
\item for each $N$, after quotienting by the fields $W^{(s)}$ with
  $s>N$, the induced OPE formulas on
  $W^{(2)},\dots,W^{(N)}$ agree with the principal finite-type stage
  $W_N$.
\end{enumerate}
Then the closed factorization ideals
\[
I_{>N}\mathcal{F}_\infty
= \langle W^{(s)} \mid s>N\rangle_{\mathrm{fact}}
\]
form a compatible principal-stage quotient system.  In particular,
Proposition~\ref{prop:winfty-higher-spin-ideal-criterion} applies, and
the resulting quotients recover the principal finite-type stages.
\end{proposition}

\begin{proof}
Spin-triangularity (1) closes the quotient OPE on generators $\le N$; (2) preserves the ideal under all operations; (3) identifies the quotient with $W_N$.  Nesting of ideals gives compatibility for varying $N$.
\end{proof}

\begin{proposition}[Coefficient-level DS criterion for principal-stage
\texorpdfstring{$W_\infty$}{W_infty} quotients;
\ClaimStatusProvedHere]
\label{prop:winfty-ds-coefficient-criterion}
Fix $N \ge 2$ and let
$\mathcal{F}_{\le N}:=\mathcal{F}_\infty/I_{>N}\mathcal{F}_\infty$
be a quotient from
Proposition~\ref{prop:winfty-spin-triangular-ideals}.
If the quotient is strongly generated by $W^{(2)},\dots,W^{(N)}$ with
OPE coefficients matching the principal DS formulas for $W_N$, no
additional local relations, and induced bar operations coinciding with
the finite-stage package, then $\mathcal{F}_{\le N}$ identifies with
$W_N$ and
Proposition~\ref{prop:winfty-higher-spin-ideal-criterion} applies.
\end{proposition}

\begin{proof}
The hypotheses supply the same generators, OPE, and bar data as $W_N$; the reconstruction principle gives the identification.
\end{proof}

\begin{proposition}[Local-coefficient criterion for principal-stage
\texorpdfstring{$W_\infty$}{W_infty} quotients;
\ClaimStatusProvedHere]
\label{prop:winfty-ds-local-coefficient-criterion}
Fix $N \ge 2$ and let
$\mathcal{F}_{\le N}:=\mathcal{F}_\infty/I_{>N}\mathcal{F}_\infty$
be as in
Proposition~\ref{prop:winfty-spin-triangular-ideals}.  If the local
OPE coefficients $C_{s,t}^{u;m,n}(N)$ agree with the principal DS data,
translation descendants generate all local relations, and bar operations
match, then Proposition~\ref{prop:winfty-ds-coefficient-criterion}
applies and the quotient identifies with $W_N$.
\end{proposition}

\begin{proof}
Immediate from Proposition~\ref{prop:winfty-ds-coefficient-criterion}.
\end{proof}

\begin{proposition}[Residue-coefficient identity criterion for
principal-stage \texorpdfstring{$W_\infty$}{W_infty} quotients;
\ClaimStatusProvedHere]
\label{prop:winfty-ds-residue-identity-criterion}
Fix $N \ge 2$ and let
$\mathcal{F}_{\le N}:=\mathcal{F}_\infty/I_{>N}\mathcal{F}_\infty$
be as in Proposition~\ref{prop:winfty-spin-triangular-ideals}.
If $\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(N)
= \mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(N)$
for every admissible tuple and the quotient OPE and bar operations are
entirely determined by these residue coefficients, then
Proposition~\ref{prop:winfty-ds-local-coefficient-criterion} applies
and the quotient identifies with $W_N$.
\end{proposition}

\begin{proof}
Immediate from Proposition~\ref{prop:winfty-ds-local-coefficient-criterion}.
\end{proof}

\begin{proposition}[Generator-seed criterion for principal-stage
\texorpdfstring{$W_\infty$}{W_infty} residue identities;
\ClaimStatusProvedHere]
\label{prop:winfty-ds-generator-seed}
Fix $N \ge 2$ and let
\[
\mathcal{F}_{\le N}:=\mathcal{F}_\infty/I_{>N}\mathcal{F}_\infty
\]
be as in
Proposition~\ref{prop:winfty-ds-residue-identity-criterion}.  Assume:
\begin{enumerate}
\item $\mathcal{F}_{\le N}$ is strongly generated by
  $W^{(2)},\dots,W^{(N)}$;
\item for each pair of generators $W^{(s)},W^{(t)}$ with
  $2 \le s,t \le N$, the primary residue coefficients
  \[
  \mathsf{C}^{\mathrm{res}}_{s,t;u;0,n}(N)
  \]
  agree with the principal Drinfeld--Sokolov coefficients
  $\mathsf{C}^{\mathrm{DS}}_{s,t;u;0,n}(N)$ for every visible pole order
  and target spin~$u$;
\item translation commutes with the residue extraction formulas, so all
  descendant coefficients are obtained from the primary ones by
  repeated application of $\partial$; and
\item the bar operations are generated from the same residue calculus
  and therefore are determined by those translated coefficient
  families.
\end{enumerate}
Then the full mode-by-mode identities
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(N)
=\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(N)
\]
hold for all admissible indices.  Consequently the hypotheses of
Proposition~\ref{prop:winfty-ds-residue-identity-criterion} are
satisfied.
\end{proposition}

\begin{proof}
Primary generator agreement propagates to all descendants by translation (assumption~(3)), and strong generation (assumption~(1)) plus bar recovery (assumption~(4)) identify the full coefficient family, verifying Proposition~\ref{prop:winfty-ds-residue-identity-criterion}.
\end{proof}

\begin{corollary}[Finite primary seed set for principal-stage
\texorpdfstring{$W_\infty$}{W_infty} comparison;
\ClaimStatusProvedHere]
\label{cor:winfty-ds-finite-seed-set}
Fix $N \ge 2$ and define the finite index set
\[
\mathcal{I}_N:=
\left\{
(s,t,u,n)\ \middle|\
\begin{array}{l}
2 \le s \le t \le N,\\
2 \le u \le \min(N,s+t-1),\\
1 \le n \le s+t-u
\end{array}
\right\}.
\]
Assume the hypotheses of
Proposition~\ref{prop:winfty-ds-generator-seed}.  Then it is enough to
check the primary identities
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;0,n}(N)
=\mathsf{C}^{\mathrm{DS}}_{s,t;u;0,n}(N)
\qquad\text{for all } (s,t,u,n)\in\mathcal{I}_N.
\]
These finitely many checks imply the full residue/OPE identity package
required by
Proposition~\ref{prop:winfty-ds-residue-identity-criterion}.
\end{corollary}

\begin{proof}
Spin-triangularity implies that for fixed $s,t \le N$ only target spins
$u \le s+t-1$ and pole orders $n \le s+t-u$ can appear.  Since the
stage quotient discards spins $>N$, the admissible tuples are exactly
those in $\mathcal{I}_N$, hence finite.

Proposition~\ref{prop:winfty-ds-generator-seed} shows that agreement on
these primary generator coefficients propagates by translation to every
descendant coefficient and therefore to the full residue/bar package.
\end{proof}

\begin{corollary}[First principal-stage seed packets for
\texorpdfstring{$W_\infty$}{W_infty} comparison;
\ClaimStatusProvedHere]
\label{cor:winfty-ds-lowstage-seeds}
The finite seed sets of
Corollary~\ref{cor:winfty-ds-finite-seed-set} begin as follows:
\[
\mathcal{I}_2
=\{(2,2,2,1),(2,2,2,2)\},
\]
and
\begin{align*}
\mathcal{I}_3
= {} & \{(2,2,2,1),(2,2,2,2),(2,2,3,1)\} \\
& \sqcup\{(2,3,2,1),(2,3,2,2),(2,3,2,3),(2,3,3,1),(2,3,3,2)\} \\
& \sqcup\{(3,3,2,1),(3,3,2,2),(3,3,2,3),(3,3,2,4), \\
& \qquad (3,3,3,1),(3,3,3,2),(3,3,3,3)\}.
\end{align*}
In particular, the first genuinely new infinite-generator stage beyond
the theorematic Virasoro block is the stage-$3$ packet of fifteen
primary coefficients: the two Virasoro coefficients, the single
vanishing $W^{(2)}W^{(2)}\to W^{(3)}$ coefficient, five mixed
$W^{(2)}$/$W^{(3)}$ coefficients, and seven $W^{(3)}$ self-coupling
coefficients.
\end{corollary}

\begin{proof}
For $N=2$, the defining inequalities for $\mathcal{I}_N$ force
$s=t=u=2$ and $1\le n\le 2$, giving exactly the two displayed tuples.
For $N=3$, the admissible ordered pairs of generator spins are
$(2,2)$, $(2,3)$, and $(3,3)$.  The inequalities
\[
2\le u\le \min(3,s+t-1),
\qquad
1\le n\le s+t-u
\]
then give the displayed decomposition into the three corresponding
blocks.  The final sentence is simply a repackaging of those tuples by
source pair and target spin.
\end{proof}

\begin{proposition}[Incremental interacting packet from stage
\texorpdfstring{$N$}{N} to stage \texorpdfstring{$N{+}1$}{N+1};
\ClaimStatusProvedHere]
\label{prop:winfty-ds-stage-growth-packet}
Fix $N \ge 3$ and let $\mathcal{I}_N$ and $\mathcal{I}_{N+1}$ be the
seed packets of Corollary~\ref{cor:winfty-ds-finite-seed-set}.  Write
\[
\mathcal{I}_{N+1}^{\mathrm{Vir,new}}
:=
\mathcal{I}_{N+1}^{\mathrm{Vir}}\setminus \mathcal{I}_N
=
\{(2,N{+}1,u,n)\in \mathcal{I}_{N+1}\},
\]
and define the incremental interacting packet
\[
\mathcal{J}_{N+1}
:=
\mathcal{I}_{N+1}\setminus
\bigl(\mathcal{I}_N\sqcup \mathcal{I}_{N+1}^{\mathrm{Vir,new}}\bigr).
\]
Assume the hypotheses of
Proposition~\ref{prop:winfty-ds-generator-seed}.  Then:
\begin{enumerate}
\item the coefficients indexed by $\mathcal{I}_N$ are exactly the
  stage-$N$ packet identities;
\item the coefficients indexed by
  $\mathcal{I}_{N+1}^{\mathrm{Vir,new}}$ are determined by the exact
  stress-tensor action on the new generator $W^{(N+1)}$;
\item the genuinely new interacting stage-$(N+1)$ packet is therefore
  exactly $\mathcal{J}_{N+1}$, and it decomposes as the disjoint union
  \[
  \mathcal{J}_{N+1}
  =
  \mathcal{J}_{N+1}^{\mathrm{tail}}
  \sqcup
  \mathcal{J}_{N+1}^{\mathrm{mix}}
  \sqcup
  \mathcal{J}_{N+1}^{\mathrm{self}},
  \]
  where
  \[
  \mathcal{J}_{N+1}^{\mathrm{tail}}
  :=
  \{(s,t,N{+}1,n)\in\mathcal{I}_{N+1}\mid 3\le s\le t\le N\},
  \]
  \[
  \mathcal{J}_{N+1}^{\mathrm{mix}}
  :=
  \{(s,N{+}1,u,n)\in\mathcal{I}_{N+1}\mid 3\le s\le N,\ 2\le u\le N{+}1\},
  \]
  \[
  \mathcal{J}_{N+1}^{\mathrm{self}}
  :=
  \{(N{+}1,N{+}1,u,n)\in\mathcal{I}_{N+1}\mid 2\le u\le N{+}1\}.
  \]
\end{enumerate}
Consequently, once the stage-$N$ packet identities on $\mathcal{I}_N$
are known, the stage-$(N+1)$ comparison is equivalent to matching the
coefficients on the incremental interacting packet $\mathcal{J}_{N+1}$.
For $N=3$, this is exactly the stage-$4$ residual packet of
Proposition~\ref{prop:winfty-ds-stage4-residual-packet}.
\end{proposition}

\begin{proof}
Since $\mathcal{I}_N\subset \mathcal{I}_{N+1}$, new tuples have at least one index equal to $N{+}1$.  Those with $s=2$ form $\mathcal{I}_{N+1}^{\mathrm{Vir,new}}$; the complement $\mathcal{J}_{N+1}$ (with $s\geq 3$) splits exhaustively into the three displayed blocks by whether the new index appears in $u$, $t$, or both.
\end{proof}

\begin{corollary}[Top-pole/parity reduction of the incremental
\texorpdfstring{$W_\infty$}{W_infty} stage-growth packet;
\ClaimStatusProvedHere]
\label{cor:winfty-ds-stage-growth-top-parity}
Fix $N \ge 3$ and assume the hypotheses of
Proposition~\ref{prop:winfty-ds-stage-growth-packet},
Proposition~\ref{prop:winfty-ds-primary-top-pole}, and
Proposition~\ref{prop:winfty-ds-self-ope-parity}.  Let
\[
\mathcal{J}_{N+1}^{\mathrm{top}}
:=
\{(s,t,u,s+t-u)\in \mathcal{J}_{N+1}\},
\]
and remove the odd self-OPE top-pole entries by setting
\[
\mathcal{J}_{N+1}^{\mathrm{red}}
:=
\mathcal{J}_{N+1}^{\mathrm{top}}
\setminus
\bigl\{(s,s,u,2s-u)\in\mathcal{J}_{N+1}^{\mathrm{top}}
\mid 2s-u \text{ odd}\bigr\}.
\]
Then, once the stage-$N$ packet identities on $\mathcal{I}_N$ are
known, the stage-$(N+1)$ comparison closes as soon as the identities on
the reduced incremental packet
$\mathcal{J}_{N+1}^{\mathrm{red}}$ are proved.

For $N=3$, one has
\[
\mathcal{J}_4^{\mathrm{red}}
=
\mathcal{J}_4^{\mathrm{par}},
\]
so this is exactly the six-entry stage-$4$ block of
Corollary~\ref{cor:winfty-ds-stage4-parity-packet}.  The additional
contraction of that six-entry block to the four higher-spin channels is
conjecturally controlled by
Conjecture~\ref{conj:winfty-stage4-ward-inheritance}.
\end{corollary}

\begin{proof}
Top-pole primaryity (Proposition~\ref{prop:winfty-ds-primary-top-pole}) and odd self-OPE parity (Proposition~\ref{prop:winfty-ds-self-ope-parity}) reduce $\mathcal{J}_{N+1}$ to $\mathcal{J}_{N+1}^{\mathrm{red}}$.  For $N=3$ this recovers the stage-$4$ parity packet.
\end{proof}

\begin{corollary}[First reduced incremental packet beyond
\texorpdfstring{$\mathcal{I}_4$}{I4}; \ClaimStatusProvedHere]
\label{cor:winfty-ds-stage5-reduced-packet}
Assume the hypotheses of
Corollary~\ref{cor:winfty-ds-stage-growth-top-parity} with $N=4$.
Then the first reduced incremental packet beyond the stage-$4$ block is
\[
\mathcal{J}_5^{\mathrm{red}}
=
\Bigl\{
(3,4;5;0,2)
\Bigr\}
\sqcup
\Bigl\{
(3,5;2;0,6),\,
(3,5;3;0,5),\,
(3,5;4;0,4),\,
(3,5;5;0,3)
\Bigr\}
\]
\[
\sqcup
\Bigl\{
(4,5;2;0,7),\,
(4,5;3;0,6),\,
(4,5;4;0,5),\,
(4,5;5;0,4)
\Bigr\}
\sqcup
\Bigl\{
(5,5;2;0,8),\,
(5,5;4;0,6)
\Bigr\}.
\]
In particular,
\[
|\mathcal{J}_5^{\mathrm{red}}|=11,
\]
decomposed as one tail channel, two four-entry mixed blocks, and two
self-coupling channels.
\end{corollary}

\begin{proof}
Enumerate the tail, mixed, and self blocks of $\mathcal{J}_5$ from Proposition~\ref{prop:winfty-ds-stage-growth-packet}; apply top-pole primaryity and odd self-OPE parity to each.  The surviving entries are exactly the displayed eleven tuples.
\end{proof}

\begin{proposition}[Primary top-pole criterion for generator seed
packets; \ClaimStatusProvedHere]
\label{prop:winfty-ds-primary-top-pole}
Fix $N \ge 2$ and assume the hypotheses of
Proposition~\ref{prop:winfty-ds-generator-seed}.  Assume moreover that
for each $2 \le u \le N$ the strong generator $W^{(u)}$ is primary of
conformal weight $u$ with respect to the Virasoro field
$T:=W^{(2)}$, and that the local OPE is decomposed into conformal
families of these primary generators and their translation
descendants.

Then for every visible triple $(s,t,u)$ with
\[
2 \le s \le t \le N,
\qquad
2 \le u \le \min(N,s+t-1),
\]
the primary generator $W^{(u)}$ can appear only at the top pole order
\[
n_{\max}(s,t;u):=s+t-u.
\]
Equivalently,
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;0,n}(N)
\;=\;
\mathsf{C}^{\mathrm{DS}}_{s,t;u;0,n}(N)
\;=\;0
\qquad\text{for every } 1\le n < s+t-u.
\]
Consequently the primary seed set of
Corollary~\ref{cor:winfty-ds-finite-seed-set} reduces further to the
top-pole subset
\[
\mathcal{I}_N^{\mathrm{top}}
:=\{(s,t,u,s+t-u)\in \mathcal{I}_N\}.
\]
\end{proposition}

\begin{proof}
Because $W^{(s)}$, $W^{(t)}$, and $W^{(u)}$ are primary fields of
weights $s$, $t$, and $u$, conformal covariance organizes the
$W^{(u)}$-family inside the OPE
$W^{(s)}(z)W^{(t)}(w)$ as one primary coefficient multiplying
$W^{(u)}(w)$ at pole order $s+t-u$, together with the translation
descendants $\partial^m W^{(u)}(w)$ at the lower poles
$s+t-u-m$.  The undifferentiated primary field therefore occurs only at
the top pole order $n=s+t-u$.

In the notation of
Proposition~\ref{prop:winfty-ds-generator-seed}, the coefficients
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;0,n}(N),
\qquad
\mathsf{C}^{\mathrm{DS}}_{s,t;u;0,n}(N)
\]
record the coefficients of the undifferentiated primary generator
$W^{(u)}$ itself.  Hence those coefficients vanish for all lower pole
orders $n<s+t-u$, both on the residue side and on the principal
Drinfeld--Sokolov side.  This proves the displayed vanishing and
identifies the reduced top-pole seed set $\mathcal{I}_N^{\mathrm{top}}$.
\end{proof}

\begin{proposition}[Odd top-pole vanishing for identical even
generators; \ClaimStatusProvedHere]
\label{prop:winfty-ds-self-ope-parity}
Fix $N \ge 2$ and assume the hypotheses of
Proposition~\ref{prop:winfty-ds-primary-top-pole}.  Assume moreover
that the strong generators $W^{(2)},\dots,W^{(N)}$ are even fields.
Then for every visible self-coupling triple $(s,s,u)$ one has
\[
\mathsf{C}^{\mathrm{res}}_{s,s;u;0,\,2s-u}(N)
=
\mathsf{C}^{\mathrm{DS}}_{s,s;u;0,\,2s-u}(N)
=0
\qquad\text{whenever } 2s-u \text{ is odd}.
\]
Equivalently, for identical even generators the top-pole primary
coefficient can be nonzero only when the top pole order is even.
\end{proposition}

\begin{proof}
Let $A:=W^{(s)}$ and set $m:=2s-u-1$, so the top-pole primary
coefficient of the target generator $W^{(u)}$ in the self-OPE
$A(z)A(w)$ is the $A_{(m)}A$ term.  Because $A$ is even, the
vertex-algebra skew-symmetry formula gives
\[
A_{(m)}A
=
\sum_{j\ge 0}\frac{(-1)^{m+j+1}}{j!}\,\partial^j(A_{(m+j)}A).
\]
By Proposition~\ref{prop:winfty-ds-primary-top-pole}, the
undifferentiated primary generator channel occurs only at the top pole,
so the terms with $j>0$ do not contribute to the same primary
coefficient.  Therefore the primary coefficient satisfies
\[
A_{(m)}A = (-1)^{m+1}A_{(m)}A = (-1)^{2s-u}A_{(m)}A.
\]
If $2s-u$ is odd, this becomes $A_{(m)}A=-A_{(m)}A$, hence the
coefficient vanishes.  The same skew-symmetry identity holds on the
principal Drinfeld--Sokolov side, so both displayed coefficients
vanish.
\end{proof}

\begin{proposition}[Stage-\texorpdfstring{$3$}{3} principal packet from the explicit
\texorpdfstring{$W_3$}{W3} OPE; \ClaimStatusProvedHere]
\label{prop:winfty-ds-stage3-explicit-packet}
Fix $N=3$ and write
\[
T:=W^{(2)},
\qquad
W:=W^{(3)}.
\]
For the principal stage $W_3$, the primary residue coefficients on the
seed set $\mathcal{I}_3$ are completely determined by the explicit
$W_3$ OPE package:
\begin{enumerate}
\item the Virasoro block
  \[
  T(z)T(w)\sim \frac{c/2}{(z-w)^4}
  +\frac{2T(w)}{(z-w)^2}
  +\frac{\partial T(w)}{z-w};
  \]
\item the primary-field block
  \[
  T(z)W(w)\sim \frac{3W(w)}{(z-w)^2}
  +\frac{\partial W(w)}{z-w};
  \]
\item the complete $W$-$W$ block
  \begin{align*}
  W(z)W(w)\sim {} &
  \frac{c/3}{(z-w)^6}
  +\frac{2T(w)}{(z-w)^4}
  +\frac{\partial T(w)}{(z-w)^3} \\
  & +
  \frac{\frac{3}{10}\partial^2T(w)
  +\frac{16}{22+5c}\Lambda(w)}{(z-w)^2}
  +\frac{\frac{1}{15}\partial^3T(w)
  +\frac{8}{22+5c}\partial\Lambda(w)}{z-w},
  \end{align*}
  with $\Lambda={:}TT{:}-\frac{3}{10}\partial^2T$.
\end{enumerate}
More precisely, among the fifteen tuples in $\mathcal{I}_3$, only the
three primary coefficients
\[
\mathsf{C}^{\mathrm{DS}}_{2,2;2;0,2}(3)=2,
\qquad
\mathsf{C}^{\mathrm{DS}}_{2,3;3;0,2}(3)=3,
\qquad
\mathsf{C}^{\mathrm{DS}}_{3,3;2;0,4}(3)=2
\]
are nonzero; the remaining twelve coefficients in $\mathcal{I}_3$
vanish.  Consequently the stage-$3$ comparison problem is equivalent to
matching these three numbers and the twelve forced vanishings, after
which translation recovers all descendant coefficients.
\end{proposition}

\begin{proof}
The seed set $\mathcal{I}_3$ was written explicitly in
Corollary~\ref{cor:winfty-ds-lowstage-seeds}.  We read its coefficients
off from the explicit $W_3$ OPE package.

For the pair $(T,T)$, the only primary generator appearing in the
Virasoro OPE is $T$ itself at pole order $2$, with coefficient $2$.
The pole-order-$1$ term is $\partial T$, hence a descendant, and there
is no primary target of spin $3$.  Therefore
\[
\mathsf{C}^{\mathrm{DS}}_{2,2;2;0,2}(3)=2,
\qquad
\mathsf{C}^{\mathrm{DS}}_{2,2;2;0,1}(3)=
\mathsf{C}^{\mathrm{DS}}_{2,2;3;0,1}(3)=0.
\]

For the mixed pair $(T,W)$, the primary-field OPE shows that the only
primary target is $W$ at pole order $2$, with coefficient $3$.  The
pole-order-$1$ term is $\partial W$, hence a descendant, and no primary
target of spin $2$ appears.  Thus
\[
\mathsf{C}^{\mathrm{DS}}_{2,3;3;0,2}(3)=3,
\]
and all four remaining mixed primary coefficients in $\mathcal{I}_3$
vanish.

For the pair $(W,W)$, the complete $W$-$W$ OPE has primary generator
target $T$ only at pole order $4$, again with coefficient $2$.  The
terms at pole orders $3,2,1$ are the descendants
$\partial T$, $\partial^2 T$, and $\partial^3 T$, while the
$\Lambda$-terms lie in conformal weight $4$ and therefore outside the
generator seed set $\mathcal{I}_3$.  No primary target of spin $3$
appears.  Hence
\[
\mathsf{C}^{\mathrm{DS}}_{3,3;2;0,4}(3)=2,
\]
and the other seven $(W,W)$-entries in $\mathcal{I}_3$ vanish.

This accounts for all fifteen tuples in $\mathcal{I}_3$.  The final
sentence is then exactly the translation-propagation statement of
Proposition~\ref{prop:winfty-ds-generator-seed}.
\end{proof}

\begin{proposition}[Stage-\texorpdfstring{$4$}{4} residual packet after the theorematic
\texorpdfstring{$W_3$}{W3} sector; \ClaimStatusProvedHere]
\label{prop:winfty-ds-stage4-residual-packet}
Fix $N=4$ and let $\mathcal{I}_4$ be the primary seed set of
Corollary~\ref{cor:winfty-ds-finite-seed-set}.  Write
\[
\mathcal{I}_4^{\mathrm{Vir}}
:=\{(s,t,u,n)\in\mathcal{I}_4 \mid s=2\},
\qquad
\mathcal{I}_4^{W_3}
:=\{(3,3,u,n)\in\mathcal{I}_4 \mid u\le 3\}.
\]
Then every primary coefficient indexed by
\[
\mathcal{I}_4^{\mathrm{Vir}}\sqcup \mathcal{I}_4^{W_3}
\]
is already determined by the exact stress-tensor action on
$W^{(2)},W^{(3)},W^{(4)}$ together with the explicit stage-$3$
\texorpdfstring{$W_3$}{W3} packet of
Proposition~\ref{prop:winfty-ds-stage3-explicit-packet}.  The only
genuinely new stage-$4$ primary coefficients are therefore the residual
packet
\[
\mathcal{J}_4
:=\mathcal{I}_4\setminus
\bigl(\mathcal{I}_4^{\mathrm{Vir}}\sqcup \mathcal{I}_4^{W_3}\bigr),
\]
which has cardinality $29$ and decomposes as
\[
\mathcal{J}_4
=\{(3,3,4,1),(3,3,4,2)\}
\sqcup \mathcal{J}_4^{3,4}
\sqcup \mathcal{J}_4^{4,4},
\]
where
\begin{align*}
\mathcal{J}_4^{3,4}
={} & \{(3,4,2,1),(3,4,2,2),(3,4,2,3),(3,4,2,4),(3,4,2,5)\} \\
& \sqcup \{(3,4,3,1),(3,4,3,2),(3,4,3,3),(3,4,3,4)\} \\
& \sqcup \{(3,4,4,1),(3,4,4,2),(3,4,4,3)\},
\end{align*}
and
\begin{align*}
\mathcal{J}_4^{4,4}
={} & \{(4,4,2,1),(4,4,2,2),(4,4,2,3),(4,4,2,4),(4,4,2,5),(4,4,2,6)\} \\
& \sqcup \{(4,4,3,1),(4,4,3,2),(4,4,3,3),(4,4,3,4),(4,4,3,5)\} \\
& \sqcup \{(4,4,4,1),(4,4,4,2),(4,4,4,3),(4,4,4,4)\}.
\end{align*}
Consequently, the stage-$4$ comparison problem is equivalent to
matching these $29$ coefficients.  Once that packet agrees with the
principal Drinfeld--Sokolov coefficients, translation again recovers
all descendant coefficients.
\end{proposition}

\begin{proof}
All source-$2$ tuples lie in $\mathcal{I}_4^{\mathrm{Vir}}$ (stress-tensor action); the $(3,3)$ tuples with $u\le 3$ lie in $\mathcal{I}_4^{W_3}$ (stage-$3$ packet).  Enumerating the remaining admissible tuples for $(3,3,4)$, $(3,4)$, and $(4,4)$ gives the displayed decomposition with cardinality $2+12+15=29$.
\end{proof}

\begin{computation}[Stage-\texorpdfstring{$4$}{4} seed set and residual packet verification]
\label{comp:winfty-stage4-seed-verification}
\index{MC4!W-infinity stage-4 verification}
The seed set cardinalities and residual decomposition of
Proposition~\ref{prop:winfty-ds-stage4-residual-packet} have been
verified computationally
(\texttt{compute/\allowbreak lib/\allowbreak w4\_stage4\_coefficients.py},
$74$~tests):
\begin{itemize}
\item $|\mathcal{I}_4| = 54$,
  $|\mathcal{I}_4^{\mathrm{Vir}}| = 18$,
  $|\mathcal{I}_4^{W_3}| = 7$,
  $|\mathcal{J}_4| = 29$;
\item Residual decomposition: $(3,3)$-tail of size~$2$,
  $\mathcal{J}_4^{3,4}$ of size~$12$ (sub-decomposition $5+4+3$),
  $\mathcal{J}_4^{4,4}$ of size~$15$ (sub-decomposition $6+5+4$);
\item Stage-$3$ packet reproduced:
  $\mathsf{C}^{\mathrm{DS}}_{2,2;2;0,2} = 2$,
  $\mathsf{C}^{\mathrm{DS}}_{2,3;3;0,2} = 3$,
  $\mathsf{C}^{\mathrm{DS}}_{3,3;2;0,4} = 2$ (three nonzero,
  twelve vanishing);
\item Complementarity sum:
  $c(k) + c(-k-8) = 246$ (constant in~$k$);
\item Universal $T$-coupling pattern:
  $\mathsf{C}_{s,s;2;0,2s-2} = 2$ confirmed for $s = 2, 3$;
  predicted for $s = 4$.
\end{itemize}
\end{computation}

\begin{corollary}[Stage-\texorpdfstring{$4$}{4} top-pole packet after primaryity;
\ClaimStatusProvedHere]
\label{cor:winfty-ds-stage4-top-pole-packet}
Assume the hypotheses of
Proposition~\ref{prop:winfty-ds-stage4-residual-packet} and
Proposition~\ref{prop:winfty-ds-primary-top-pole}.  Then the residual
stage-$4$ packet $\mathcal{J}_4$ reduces further to the top-pole subset
\[
\mathcal{J}_4^{\mathrm{top}}
=\{(3,3,4,2),(3,4,2,5),(3,4,3,4),(3,4,4,3),
(4,4,2,6),(4,4,3,5),(4,4,4,4)\},
\]
which has cardinality $7$.  Equivalently, among the `29` residual
stage-$4$ primary coefficients, only these seven top-pole coefficients
can be nonzero; the remaining twenty-two coefficients in
$\mathcal{J}_4$ vanish by primaryity.

Consequently, the genuinely new principal stage-$4$ comparison problem
is equivalent to matching these seven coefficients with the
Drinfeld--Sokolov data.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:winfty-ds-primary-top-pole} retains only the top pole $n=s+t-u$ for each triple, giving the seven displayed tuples; all lower-pole entries vanish.
\end{proof}

\begin{corollary}[Stage-\texorpdfstring{$4$}{4} parity-compressed packet;
\ClaimStatusProvedHere]
\label{cor:winfty-ds-stage4-parity-packet}
Assume the hypotheses of
Corollary~\ref{cor:winfty-ds-stage4-top-pole-packet} and
Proposition~\ref{prop:winfty-ds-self-ope-parity}.  Then the stage-$4$
top-pole packet reduces further to
\[
\mathcal{J}_4^{\mathrm{par}}
=\{(3,3,4,2),(3,4,2,5),(3,4,3,4),(3,4,4,3),
(4,4,2,6),(4,4,4,4)\},
\]
which has cardinality $6$.  Equivalently, among the `7` top-pole
coefficients of
Corollary~\ref{cor:winfty-ds-stage4-top-pole-packet}, the odd self-OPE
entry $(4,4,3,5)$ vanishes by skew-symmetry.  Hence the residual
stage-$4$ comparison problem is equivalent to matching these six
coefficients, together with the forced vanishing of the remaining `23`
entries in the original residual packet $\mathcal{J}_4$.
\end{corollary}

\begin{proof}
Among the seven top-pole entries, the only odd self-OPE top pole is $(4,4,3,5)$; Proposition~\ref{prop:winfty-ds-self-ope-parity} kills it, leaving six.
\end{proof}

\begin{corollary}[Stage-\texorpdfstring{$4$}{4} packet as three local OPE blocks;
\ClaimStatusProvedHere]
\label{cor:winfty-ds-stage4-ope-blocks}
Assume the hypotheses of
Corollary~\ref{cor:winfty-ds-stage4-parity-packet}.  Then the residual
principal stage-$4$ comparison problem is equivalent to matching the
six coefficients in the three top-pole OPE blocks
\begin{align*}
W^{(3)}(z)W^{(3)}(w)
&\sim
\frac{c_{334}\,W^{(4)}(w)}{(z-w)^2}
\quad\text{mod the theorematic $W_3$ sector and descendants},\\
W^{(3)}(z)W^{(4)}(w)
&\sim
\frac{c_{342}\,W^{(2)}(w)}{(z-w)^5}
+\frac{c_{343}\,W^{(3)}(w)}{(z-w)^4}
+\frac{c_{344}\,W^{(4)}(w)}{(z-w)^3}\\
&\qquad
\quad\text{mod descendants},\\
W^{(4)}(z)W^{(4)}(w)
&\sim
\frac{c_{442}\,W^{(2)}(w)}{(z-w)^6}
+\frac{c_{444}\,W^{(4)}(w)}{(z-w)^4}\\
&\qquad
\quad\text{mod the theorematic Virasoro sector and descendants}.
\end{align*}
More precisely,
\[
c_{334}=\mathsf{C}_{3,3;4;0,2},
\qquad
(c_{342},c_{343},c_{344})
\!=\!
\bigl(
\mathsf{C}_{3,4;2;0,5},
\mathsf{C}_{3,4;3;0,4},
\mathsf{C}_{3,4;4;0,3}
\bigr),
\]
and
\[
(c_{442},c_{444})
=(\mathsf{C}_{4,4;2;0,6},\mathsf{C}_{4,4;4;0,4}),
\]
where either the residue coefficients
$\mathsf{C}^{\mathrm{res}}$ or the principal Drinfeld--Sokolov
coefficients $\mathsf{C}^{\mathrm{DS}}$ may be used.  Equivalently, the
live stage-$4$ frontier is one new coefficient in the $(3,3)$ block,
three in the mixed $(3,4)$ block, and two in the even $(4,4)$ block.
\end{corollary}

\begin{proof}
Group the six parity-compressed tuples by source pair: $(3,3)$ contributes one, $(3,4)$ three, $(4,4)$ two.
\end{proof}

\begin{corollary}[Stage-\texorpdfstring{$4$}{4} frontier as one mixed block and three
self-coupling scalars; \ClaimStatusProvedHere]
\label{cor:winfty-ds-stage4-mixed-self-split}
Assume the hypotheses of
Corollary~\ref{cor:winfty-ds-stage4-ope-blocks}.  Then the residual
principal stage-$4$ comparison decomposes as:
\begin{enumerate}[label=\textup{(\roman*)}]
\item a self-coupling sector consisting of the three scalar top-pole
  coefficients
  \[
  c_{334},\qquad c_{442},\qquad c_{444};
  \]
\item a mixed higher-spin sector consisting of the single
  $W^{(3)}$-$W^{(4)}$ block
  \[
  (c_{342},c_{343},c_{344}).
  \]
\end{enumerate}
Equivalently, the only genuinely mixed stage-$4$ higher-spin data are
the three coefficients in the $W^{(3)}(z)W^{(4)}(w)$ block; the
remaining three live coefficients come from the self-couplings
$W^{(3)}$-$W^{(3)}$ and $W^{(4)}$-$W^{(4)}$.
\end{corollary}

\begin{proof}
Regroup: $(3,3)$ and $(4,4)$ give the self-coupling sector; $(3,4)$ is the mixed sector.
\end{proof}

\begin{proposition}[Mixed top-pole swap parity for even generators;
\ClaimStatusProvedHere]
\label{prop:winfty-ds-mixed-top-pole-swap}
Fix $N \ge 2$ and assume the hypotheses of
Proposition~\ref{prop:winfty-ds-primary-top-pole}.  Assume moreover
that the strong generators $W^{(2)},\dots,W^{(N)}$ are even fields.
For every visible mixed triple $(s,t,u)$ with $2 \le s < t \le N$ and
$u \le \min(N,s+t-1)$, write
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u}(N)
:=
\mathsf{C}^{\mathrm{res}}_{s,t;u;0,\,s+t-u}(N),
\qquad
\mathsf{C}^{\mathrm{DS}}_{s,t;u}(N)
:=
\mathsf{C}^{\mathrm{DS}}_{s,t;u;0,\,s+t-u}(N)
\]
for the top-pole primary coefficients.  Then the reversed-order
coefficients satisfy
\[
\mathsf{C}^{\mathrm{res}}_{t,s;u}(N)
=
(-1)^{s+t-u}\mathsf{C}^{\mathrm{res}}_{s,t;u}(N),
\qquad
\mathsf{C}^{\mathrm{DS}}_{t,s;u}(N)
=
(-1)^{s+t-u}\mathsf{C}^{\mathrm{DS}}_{s,t;u}(N).
\]
Equivalently, for even primary generators the top-pole mixed
$W^{(u)}$-channel is swap-even when $s+t-u$ is even and swap-odd when
$s+t-u$ is odd.
\end{proposition}

\begin{proof}
The vertex-algebra skew-symmetry formula for even fields, combined with top-pole primaryity (Proposition~\ref{prop:winfty-ds-primary-top-pole}) to eliminate $j>0$ terms, gives $\mathsf{C}_{s,t;u}^{\mathrm{res}}=(-1)^{s+t-u}\mathsf{C}_{t,s;u}^{\mathrm{res}}$.  The same holds on the DS side.
\end{proof}

\begin{corollary}[Stage-\texorpdfstring{$4$}{4} mixed block split by swap parity;
\ClaimStatusProvedHere]
\label{cor:winfty-ds-stage4-mixed-swap-parity}
Assume the hypotheses of
Corollary~\ref{cor:winfty-ds-stage4-mixed-self-split} and
Proposition~\ref{prop:winfty-ds-mixed-top-pole-swap}.  Write
\[
W^{(4)}(z)W^{(3)}(w)
\sim
\frac{\widetilde c_{432}\,W^{(2)}(w)}{(z-w)^5}
+\frac{\widetilde c_{433}\,W^{(3)}(w)}{(z-w)^4}
+\frac{\widetilde c_{434}\,W^{(4)}(w)}{(z-w)^3}
\quad\text{mod descendants}
\]
for the reversed-order mixed block.  Then
\[
\widetilde c_{432}=-c_{342},
\qquad
\widetilde c_{433}=c_{343},
\qquad
\widetilde c_{434}=-c_{344}.
\]
Equivalently, the live mixed stage-$4$ frontier splits into one
swap-even channel $c_{343}$ and two swap-odd channels
$c_{342},c_{344}$.
\end{corollary}

\begin{proof}
Apply Proposition~\ref{prop:winfty-ds-mixed-top-pole-swap} to $(3,4,u)$ for $u=2,3,4$; the signs $(-1)^{7-u}$ give the displayed identities.
\end{proof}

\begin{proposition}[Formal mixed Virasoro-target vanishing under a
normalized two-point package; \ClaimStatusProvedHere]
\label{prop:winfty-formal-mixed-virasoro-zero}
Fix $N \ge 3$ and consider a stage-$N$ local OPE calculus with visible
primary generators $W^{(2)},\dots,W^{(N)}$, where
$T:=W^{(2)}$ is the Virasoro field.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item each visible generator $W^{(u)}$ has conformal weight $u$, the
  local OPE is decomposed into conformal families of these primary
  generators and their translation descendants, and the Virasoro Ward
  identity holds for insertions of $T$ against each visible generator;
\item for every mixed pair $2 \le s < t \le N$, the vacuum two-point
  function vanishes:
  \[
  \langle W^{(s)}(z)W^{(t)}(0)\rangle=0;
  \]
\item the stress tensor is normalized by
  \[
  \langle T(z)T(0)\rangle=\frac{c/2}{z^4}
  \qquad\text{with } c\neq 0.
  \]
\end{enumerate}
Let
\[
\mathsf{C}_{s,t;u;0,n}(N)
\]
denote the undifferentiated primary coefficient of the target
$W^{(u)}$ at pole order $n$ in this local OPE calculus.  Then for every
visible mixed pair $2 \le s < t \le N$, the top-pole stress-tensor
coefficient vanishes:
\[
\mathsf{C}_{s,t;2;0,\,s+t-2}(N)=0.
\]
Equivalently, under this normalized two-point package the
undifferentiated $W^{(2)}=T$ channel is absent from the top pole of
every mixed OPE $W^{(s)}(z)W^{(t)}(w)$ with $s\ne t$.
\end{proposition}

\begin{proof}
Mixed-weight orthogonality (assumption~\textup{(ii)}) makes $\langle T(x)A(z)B(0)\rangle = 0$.  The top-pole $T$-channel contributes $\frac{c}{2}\mathsf{C}_{s,t;2;0,s+t-2}$ to the $x^{-4}z^{-(s+t-2)}$ coefficient; since $c\neq 0$, the coefficient vanishes.
\end{proof}

\begin{proposition}[Principal Drinfeld--Sokolov vanishing of the mixed
Virasoro target; \ClaimStatusProvedHere]
\label{prop:winfty-ds-mixed-virasoro-ds-zero}
Fix $N \ge 3$ and consider the principal Drinfeld--Sokolov stage
$\mathcal{W}_N$ at a generic level with nonzero central charge $c$.
Assume the Zamolodchikov normalization and mixed-weight orthogonality
package of Theorem~\ref{thm:wn-obstruction}.  Then for every visible
mixed pair $2 \le s < t \le N$, the top-pole stress-tensor coefficient
vanishes:
\[
\mathsf{C}^{\mathrm{DS}}_{s,t;2;0,\,s+t-2}(N)=0.
\]
Equivalently, on the principal Drinfeld--Sokolov side the
undifferentiated $W^{(2)}=T$ channel is absent from the top pole of
every mixed OPE $W^{(s)}(z)W^{(t)}(w)$ with $s \ne t$.
\end{proposition}

\begin{proof}
Apply Proposition~\ref{prop:winfty-formal-mixed-virasoro-zero} to the
principal Drinfeld--Sokolov stage.  Theorem~\ref{thm:wn-obstruction}
supplies the required normalized two-point package: the visible
generators are primary, the mixed two-point functions vanish for
distinct conformal weights, and
$\langle T(z)T(0)\rangle=\frac{c/2}{z^4}$ with $c\neq 0$ at generic
level.
\end{proof}

\begin{corollary}[Stage-\texorpdfstring{$4$}{4} mixed block as one vanishing channel and a
parity pair; \ClaimStatusProvedHere]
\label{cor:winfty-ds-stage4-mixed-two-channel}
Assume the hypotheses of
Corollary~\ref{cor:winfty-ds-stage4-mixed-swap-parity} and
Proposition~\ref{prop:winfty-ds-mixed-virasoro-ds-zero}.  Then on the
principal Drinfeld--Sokolov side one has
\[
\mathsf{C}^{\mathrm{DS}}_{3,4;2;0,5}=0,
\qquad
\mathsf{C}^{\mathrm{DS}}_{4,3;2;0,5}=0.
\]
Consequently, the stage-$4$ mixed comparison problem reduces to:
\begin{enumerate}[label=\textup{(\roman*)}]
\item proving the corresponding residue-side vanishing in the
  $W^{(2)}$ target channel;
\item matching the remaining swap-even coefficient
  $\mathsf{C}_{3,4;3;0,4}$;
\item matching the remaining swap-odd coefficient
  $\mathsf{C}_{3,4;4;0,3}$.
\end{enumerate}
Equivalently, the principal mixed stage-$4$ data consist of one
theorematically zero $W^{(2)}$ target channel together with a
swap-even / swap-odd pair targeting $W^{(3)}$ and $W^{(4)}$.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:winfty-ds-mixed-virasoro-ds-zero} gives the first vanishing; swap parity (Corollary~\ref{cor:winfty-ds-stage4-mixed-swap-parity}) gives the second.
\end{proof}

\begin{proposition}[Formal self-coupling stress-tensor coefficient
under a normalized two-point package; \ClaimStatusProvedHere]
\label{prop:winfty-formal-self-t-coefficient}
Fix $N \ge 2$ and consider a stage-$N$ local OPE calculus with visible
primary generators $W^{(2)},\dots,W^{(N)}$, where
$T:=W^{(2)}$ is the Virasoro field.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item each visible generator $W^{(u)}$ has conformal weight $u$, the
  local OPE is decomposed into conformal families of these primary
  generators and their translation descendants, and the Virasoro Ward
  identity holds for insertions of $T$ against each visible generator;
\item for every visible generator $W^{(s)}$ one has the normalized
  two-point function
  \[
  \langle W^{(s)}(z)W^{(s)}(0)\rangle=\frac{c/s}{z^{2s}}
  \qquad\text{with } c\neq 0;
  \]
\item the stress tensor is normalized by
  \[
  \langle T(z)T(0)\rangle=\frac{c/2}{z^4}.
  \]
\end{enumerate}
Let
\[
\mathsf{C}_{s,s;u;0,n}(N)
\]
denote the undifferentiated primary coefficient of the target
$W^{(u)}$ at pole order $n$ in this local OPE calculus.  Then for every
visible generator $W^{(s)}$ with $2 \le s \le N$, the top-pole
stress-tensor coefficient in the self-OPE is
\[
\mathsf{C}_{s,s;2;0,\,2s-2}(N)=2.
\]
Equivalently, under this normalized two-point package the
undifferentiated $T=W^{(2)}$ channel appears in every self-OPE
$W^{(s)}(z)W^{(s)}(w)$ with the universal coefficient $2$.
\end{proposition}

\begin{proof}
Write $N_s:=c/s$.  The Virasoro Ward identity for $\langle T(x)A(z)A(0)\rangle$ with $A:=W^{(s)}$ has $x^{-4}z^{-2s+2}$ coefficient equal to $sN_s=c$.  The only undifferentiated $T$-contribution at the top pole $2s-2$ gives $\mathsf{C}_{s,s;2;0,2s-2}\cdot c/2$.  Matching and dividing by $c\neq 0$ yields $\mathsf{C}_{s,s;2;0,2s-2}=2$.
\end{proof}

\begin{proposition}[Formal converse: the universal self-coupling
\texorpdfstring{$T$}{T}-coefficient forces the normalized two-point
function; \ClaimStatusProvedHere]
\label{prop:winfty-formal-self-normalization-from-t}
Fix $N \ge 2$ and consider a stage-$N$ local OPE calculus with visible
primary generators $W^{(2)},\dots,W^{(N)}$, where
$T:=W^{(2)}$ is the Virasoro field.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item each visible generator $W^{(u)}$ has conformal weight $u$, the
  local OPE is decomposed into conformal families of these primary
  generators and their translation descendants, and the Virasoro Ward
  identity holds for insertions of $T$ against each visible generator;
\item the stress tensor is normalized by
  \[
  \langle T(z)T(0)\rangle=\frac{c/2}{z^4}
  \qquad\text{with } c\neq 0;
  \]
\item for some visible generator $W^{(s)}$ with $2 \le s \le N$, the
  top-pole stress-tensor coefficient in the self-OPE is
  \[
  \mathsf{C}_{s,s;2;0,\,2s-2}(N)=2.
  \]
\end{enumerate}
Then the self-pairing of $W^{(s)}$ is normalized by
\[
\langle W^{(s)}(z)W^{(s)}(0)\rangle=\frac{c/s}{z^{2s}}.
\]
Equivalently, under the visible Virasoro package the universal
self-coupling coefficient `2' and the Zamolodchikov normalization of
$W^{(s)}$ are equivalent.
\end{proposition}

\begin{proof}
Global conformal invariance forces $\langle A(z)A(0)\rangle = N_s z^{-2s}$.  The Ward-identity computation of Proposition~\ref{prop:winfty-formal-self-t-coefficient} gives $x^{-4}z^{-2s+2}$ coefficient $sN_s$ on one side and $\mathsf{C}_{s,s;2;0,2s-2}\cdot c/2 = c$ on the other.  Matching gives $N_s = c/s$.
\end{proof}

\begin{proposition}[Principal Drinfeld--Sokolov self-coupling
stress-tensor coefficient; \ClaimStatusProvedHere]
\label{prop:winfty-ds-self-t-coefficient}
Fix $N \ge 2$ and consider the principal Drinfeld--Sokolov stage
$\mathcal{W}_N$ at a generic level with nonzero central charge $c$.
Assume the Zamolodchikov normalization package of
Theorem~\ref{thm:wn-obstruction}.  Then for every visible generator
$W^{(s)}$ with $2 \le s \le N$, the top-pole stress-tensor coefficient
in the self-OPE is
\[
\mathsf{C}^{\mathrm{DS}}_{s,s;2;0,\,2s-2}(N)=2.
\]
Equivalently, on the principal Drinfeld--Sokolov side the
undifferentiated $T=W^{(2)}$ channel appears in every self-OPE
$W^{(s)}(z)W^{(s)}(w)$ with the universal coefficient $2$.
\end{proposition}

\begin{proof}
Apply Proposition~\ref{prop:winfty-formal-self-t-coefficient} to the
principal Drinfeld--Sokolov stage.  Theorem~\ref{thm:wn-obstruction}
supplies the required normalized two-point package, with
\[
\langle W^{(s)}(z)W^{(s)}(0)\rangle=\frac{c/s}{z^{2s}}
\qquad\text{and}\qquad
\langle T(z)T(0)\rangle=\frac{c/2}{z^4}
\]
at generic level.
\end{proof}

\begin{corollary}[Principal stage-\texorpdfstring{$4$}{4} self-coupling
\texorpdfstring{$W^{(4)}$-$W^{(4)}\to T$}{W4-W4 to T}
normalization; \ClaimStatusProvedHere]
\label{cor:winfty-ds-stage4-self-t-normalization}
In the setting of Proposition~\ref{prop:winfty-ds-self-t-coefficient},
one has
\[
\mathsf{C}^{\mathrm{DS}}_{4,4;2;0,6}=2.
\]
Equivalently, the principal stage-$4$ self-coupling
$W^{(4)}(z)W^{(4)}(w)\to T(w)$ is not free data: its top-pole
coefficient is universally fixed to `2`.
\end{corollary}

\begin{proof}
Apply Proposition~\ref{prop:winfty-ds-self-t-coefficient} with $s=4$.
\end{proof}

\begin{corollary}[Stage-\texorpdfstring{$4$}{4} principal target packet after theorematic
Virasoro-target elimination; \ClaimStatusProvedHere]
\label{cor:winfty-ds-stage4-five-plus-zero}
Assume the hypotheses of
Corollary~\ref{cor:winfty-ds-stage4-mixed-two-channel} and
Corollary~\ref{cor:winfty-ds-stage4-self-t-normalization}.  Then the
residual principal stage-$4$ target packet decomposes as:
\begin{enumerate}[label=\textup{(\roman*)}]
\item two higher-spin self-coupling targets
  \[
  c_{334},\qquad c_{444};
  \]
\item the mixed swap-even higher-spin target
  \[
  \mathsf{C}_{3,4;3;0,4};
  \]
\item the mixed swap-odd higher-spin target
  \[
  \mathsf{C}_{3,4;4;0,3};
  \]
\item the theorematic principal Virasoro-target value
  \[
  \mathsf{C}^{\mathrm{DS}}_{4,4;2;0,6}=2;
  \]
\item the theorematic principal Virasoro-target value
  \[
  \mathsf{C}^{\mathrm{DS}}_{3,4;2;0,5}=0.
  \]
\end{enumerate}
Equivalently, the standard stage-$4$ identity packet on~$\mathcal{I}_4$
splits into four higher-spin targets
\[
c_{334},\qquad c_{444},\qquad
\mathsf{C}_{3,4;3;0,4},\qquad \mathsf{C}_{3,4;4;0,3},
\]
together with two Virasoro-target channels whose principal values are
theorematically fixed to
\[
\mathsf{C}^{\mathrm{DS}}_{4,4;2;0,6}=2,
\qquad
\mathsf{C}^{\mathrm{DS}}_{3,4;2;0,5}=0,
\]
and whose residue-side contraction to four channels is the additional
package isolated in
Corollary~\ref{cor:winfty-stage4-residue-four-channel}.
\end{corollary}

\begin{proof}
Combine the mixed-self split (Corollary~\ref{cor:winfty-ds-stage4-mixed-self-split}), the mixed two-channel reduction (Corollary~\ref{cor:winfty-ds-stage4-mixed-two-channel}), and the universal $T$-coupling normalization (Corollary~\ref{cor:winfty-ds-stage4-self-t-normalization}).
\end{proof}

\begin{proposition}[Exact MC4 frontier packet for the standard
\texorpdfstring{$W_\infty$}{W_infty} tower; \ClaimStatusProvedHere]
\label{prop:winfty-mc4-frontier-package}
Let $\mathcal{W}^{\mathrm{ht}}$ be a separated complete H-level target
for $W_\infty$ satisfying the quotient-system hypotheses of
Corollary~\ref{cor:winfty-hlevel-comparison-criterion}.  Assume
moreover that the quotient residue calculus is translation compatible
and that the strong generators are even Virasoro-primary fields, so
that
Proposition~\ref{prop:winfty-ds-generator-seed},
Corollary~\ref{cor:winfty-ds-finite-seed-set},
Proposition~\ref{prop:winfty-ds-stage3-explicit-packet}, and
Corollary~\ref{cor:winfty-ds-stage4-five-plus-zero} apply.  Then:
\begin{enumerate}
\item for every finite stage $N$, the remaining H-level comparison with
  the principal Drinfeld--Sokolov stage $W_N$ reduces to the finite
  primary seed packet $\mathcal{I}_N$ of residue identities
  \[
  \mathsf{C}^{\mathrm{res}}_{s,t;u;0,n}(N)
  =\mathsf{C}^{\mathrm{DS}}_{s,t;u;0,n}(N);
  \]
\item at stage~$3$, that packet is already theorematically fixed by the
  explicit $W_3$ OPE: three nonzero primary coefficients and twelve
  forced vanishing statements;
\item at stage~$4$, after removing the theorematic Virasoro and
  $W_3$ sectors, the first genuinely open higher-spin packet is exactly
  the exact six-entry identity packet on~$\mathcal{I}_4$
  \[
  \mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(4)
  =
  \mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(4)
  \]
  in the channels
  \[
  \begin{gathered}
  (3,3;4;0,2),\qquad
  (4,4;4;0,4),\\
  (3,4;3;0,4),\qquad
  (3,4;4;0,3),\qquad
  (4,4;2;0,6),\\
  (3,4;2;0,5).
  \end{gathered}
  \]
  with the first four entries forming the residual higher-spin
  comparison packet, while the last two are Virasoro-target channels
  whose principal values are already fixed by
  Corollary~\ref{cor:winfty-ds-stage4-five-plus-zero}.
\end{enumerate}
In particular, once the H-level target and quotient system are
constructed, the standard $\mathcal{W}_\infty$ MC4 problem is not a
further stabilization theorem.  It is the finite stagewise
residue-identification problem on the packets $\mathcal{I}_N$, with the
first genuinely open higher-spin packet occurring at stage~$4$ in the
displayed six-entry identity form on~$\mathcal{I}_4$.
\end{proposition}

\begin{proof}
\textup{(1)}: Corollary~\ref{cor:winfty-hlevel-comparison-criterion} plus Proposition~\ref{prop:winfty-ds-generator-seed} and Corollary~\ref{cor:winfty-ds-finite-seed-set}.  \textup{(2)}: Proposition~\ref{prop:winfty-ds-stage3-explicit-packet}.  \textup{(3)}: Corollary~\ref{cor:winfty-ds-stage4-five-plus-zero}.
\end{proof}

\begin{corollary}[Minimal closure criterion for the standard
\texorpdfstring{$W_\infty$}{W_infty} MC4 frontier;
\ClaimStatusProvedHere]
\label{cor:winfty-stage4-closure-criterion}
Under the hypotheses of
Proposition~\ref{prop:winfty-mc4-frontier-package}, the standard
\texorpdfstring{$W_\infty$}{W_infty} H-level comparison closes once the
stagewise packet identities on~$\mathcal{I}_N$ are proved.  The first
genuinely open higher-spin packet is the exact six-entry stage-$4$
identity packet on~$\mathcal{I}_4$.  Within that packet, the residual
higher-spin channels still to be matched are
\[
\begin{gathered}
(3,3;4;0,2),\qquad
(4,4;4;0,4),\qquad
(3,4;3;0,4),\qquad
(3,4;4;0,3),
\end{gathered}
\]
while the corresponding principal Virasoro-target values are already
fixed to
\[
\mathsf{C}^{\mathrm{DS}}_{4,4;2;0,6}=2,
\qquad
\mathsf{C}^{\mathrm{DS}}_{3,4;2;0,5}=0.
\]
\end{corollary}

\begin{proof}
Corollary~\ref{cor:winfty-hlevel-comparison-criterion} upgrades
stagewise packet matching on~$\mathcal{I}_N$ to the H-level
comparison, and
Proposition~\ref{prop:winfty-mc4-frontier-package} identifies the first
open stage as the six-entry block on~$\mathcal{I}_4$.
Corollary~\ref{cor:winfty-ds-stage4-five-plus-zero} fixes the two
principal Virasoro-target values, leaving the four displayed
higher-spin channels as the residual higher-spin packet.
\end{proof}

\begin{corollary}[Constructing the completed chiral Koszul-dual
candidate for \texorpdfstring{$W_\infty$}{W_infty};
\ClaimStatusProvedHere]
\label{cor:winfty-dual-candidate-construction}
Assume the hypotheses of
Proposition~\ref{prop:winfty-mc4-frontier-package}.  Then the completed
bar object of the corresponding H-level target
$\mathcal{W}^{\mathrm{ht}}$ is quasi-isomorphic to the inverse-limit
bar object of the principal stages:
\[
\widehat{\bar B}\bigl(\mathcal{W}^{\mathrm{ht}}\bigr)
\xrightarrow{\sim}
\varprojlim_N \bar B(W_N).
\]
Its completed cobar comparison recovers
$\mathcal{W}^{\mathrm{ht}}$ up to quasi-isomorphism, and any two
principal-stage compatible H-level targets satisfying the same
stagewise packet identities determine quasi-isomorphic completed
bar-cobar objects.

Consequently, the foundational route to the chiral Koszul-dual object
of \texorpdfstring{$W_\infty$}{W_infty} is exactly:
\begin{enumerate}
\item construct a principal-stage compatible H-level or factorization
  target;
\item prove the finite packet identities on~$\mathcal{I}_N$; and
\item invoke
  Corollary~\ref{cor:winfty-hlevel-comparison-criterion} to lift the
  standard principal-stage completed bar object to that target.
\end{enumerate}
No separate infinite-generator quadratic presentation is required at
this stage.
\end{corollary}

\begin{proof}
Under the stated hypotheses,
Proposition~\ref{prop:winfty-mc4-frontier-package} identifies the
finite-stage quotient problem with the packet identities on
$\mathcal{I}_N$, while
Corollary~\ref{cor:winfty-hlevel-comparison-criterion} identifies
$\mathcal{W}^{\mathrm{ht}}$ with the standard principal-stage completed
M-level package.  The bar-cobar comparison part of that corollary
therefore gives the displayed quasi-isomorphism and the cobar recovery.
The same comparison shows that any two such H-level targets define the
same completed bar-cobar object up to quasi-isomorphism.
\end{proof}

\begin{corollary}[Stage-\texorpdfstring{$4$}{4} \texorpdfstring{$W_\infty$}{W_infty}
frontier on the Ward-normalized H-level locus;
\ClaimStatusProvedHere]
\label{cor:winfty-stage4-residue-four-channel}
Assume the hypotheses of
Proposition~\ref{prop:winfty-mc4-frontier-package}.  Assume moreover
that $\mathcal{W}^{\mathrm{ht}}$ is stage-$4$ Ward-normalized in the
sense of Definition~\ref{def:winfty-stage4-ward-normalized}.  Then the
two
Virasoro-target residue channels are theorematically fixed:
\[
\mathsf{C}^{\mathrm{res}}_{3,4;2;0,5}(4)=0,
\qquad
\mathsf{C}^{\mathrm{res}}_{4,4;2;0,6}(4)=2.
\]
Consequently the first genuinely open stage-$4$
\texorpdfstring{$W_\infty$}{W_infty} packet contracts from the six-entry
identity packet of Proposition~\ref{prop:winfty-mc4-frontier-package} to
the four-channel higher-spin identity packet
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;0,n}(4)
=
\mathsf{C}^{\mathrm{DS}}_{s,t;u;0,n}(4)
\]
in the channels
\[
\begin{gathered}
(3,3;4;0,2),\qquad
(4,4;4;0,4),\\
(3,4;3;0,4),\qquad
(3,4;4;0,3).
\end{gathered}
\]
\end{corollary}

\begin{proof}
The Ward-normalized input supplies the hypotheses of Propositions~\ref{prop:winfty-formal-mixed-virasoro-zero} and~\ref{prop:winfty-formal-self-t-coefficient}, fixing the two Virasoro-target channels; removing them leaves four higher-spin identities.
\end{proof}

\begin{proposition}[Exact missing input for the unconditional
\texorpdfstring{$W_\infty$}{W_infty} stage-\texorpdfstring{$4$}{4} contraction;
\ClaimStatusProvedHere]
\label{prop:winfty-stage4-visible-pairing-gap}
Assume the hypotheses of
Proposition~\ref{prop:winfty-mc4-frontier-package}.  Assume moreover
that the stage-$4$ quotient residue calculus on the visible generators
$W^{(2)},W^{(3)},W^{(4)}$ is decomposed into conformal families of
Virasoro-primary generators and that the Virasoro field $T:=W^{(2)}$
acts on them, including on itself, by the standard stage-$4$
Virasoro Ward identity.  Then the only additional input from the
normalized residue two-point/Ward package actually used to deduce
\[
\mathsf{C}^{\mathrm{res}}_{3,4;2;0,5}(4)=0,
\qquad
\mathsf{C}^{\mathrm{res}}_{4,4;2;0,6}(4)=2
\]
is the visible weight-$4$ self-pairing normalization
\[
\langle W^{(4)}(z)W^{(4)}(0)\rangle=\frac{c/4}{z^{8}},
\]
with the same nonzero central charge $c$ as on the principal side.
In particular, once the visible Virasoro Ward action is fixed, the open
content of Conjecture~\ref{conj:winfty-stage4-ward-inheritance} is
exactly inheritance of this weight-$4$ normalization, equivalently the
single scalar identity
\[
\mathsf{C}^{\mathrm{res}}_{4,4;2;0,6}(4)=2.
\]
\end{proposition}

\begin{proof}
Mixed-weight orthogonality and $W^{(3)}$ normalization are already forced (Propositions~\ref{prop:winfty-stage4-visible-orthogonality} and~\ref{prop:winfty-stage4-visible-w3-normalization}).  The mixed vanishing follows from Proposition~\ref{prop:winfty-formal-mixed-virasoro-zero}; the self-coupling identity reduces via Proposition~\ref{prop:winfty-formal-self-t-coefficient} to the weight-$4$ normalization.
\end{proof}

\begin{definition}[Stage-\texorpdfstring{$4$}{4} Ward-normalized standard
\texorpdfstring{$W_\infty$}{W_infty} H-level target]
\label{def:winfty-stage4-ward-normalized}
Assume the setting of
Proposition~\ref{prop:winfty-mc4-frontier-package}.  We say that the
H-level target $\mathcal{W}^{\mathrm{ht}}$ is
\emph{stage-$4$ Ward-normalized} if its induced stage-$4$ quotient
residue calculus satisfies the visible Virasoro Ward action together
with the visible weight-$4$ self-pairing normalization
\[
\langle W^{(4)}(z)W^{(4)}(0)\rangle=\frac{c/4}{z^{8}}
\]
with the same nonzero central charge $c$ as on the principal
Drinfeld--Sokolov stage.  Equivalently, by
Proposition~\ref{prop:winfty-stage4-visible-orthogonality}, the
visible generators are mixed-weight orthogonal, and by
Proposition~\ref{prop:winfty-stage4-visible-w3-normalization} the
visible $W^{(3)}$ self-pairing is already normalized as well, so the
full visible package required by
Proposition~\ref{prop:winfty-stage4-visible-pairing-gap} holds.
\end{definition}

\begin{remark}[What is still missing for an unconditional stage-\texorpdfstring{$4$}{4}
four-channel reduction]
\label{rem:winfty-stage4-four-channel-gap}
Corollary~\ref{cor:winfty-stage4-residue-four-channel} is conditional
on the additional H-level input of
Definition~\ref{def:winfty-stage4-ward-normalized}.  The
quotient-system hypotheses of
Corollary~\ref{cor:winfty-hlevel-comparison-criterion} and
Proposition~\ref{prop:winfty-mc4-frontier-package} supply compatible
finite quotients, translation compatibility, and Virasoro-primary
strong generators, but they do not by themselves identify the
visible weight-$4$ self-pairing inside that quotient residue calculus.
Mixed-weight orthogonality is already forced by the Virasoro Ward
identity, by
Proposition~\ref{prop:winfty-stage4-visible-orthogonality}.  Thus the
first unconditional standard-tower
MC4 packet remains the six-entry block of
Proposition~\ref{prop:winfty-mc4-frontier-package}.  By
Proposition~\ref{prop:winfty-stage4-visible-pairing-gap}, once the
visible Virasoro Ward action is fixed the exact remaining missing input
is Conjecture~\ref{conj:winfty-stage4-visible-diagonal-normalization},
equivalently the single scalar identity
\[
\mathsf{C}^{\mathrm{res}}_{4,4;2;0,6}(4)=2.
\]
Its package form is
Conjecture~\ref{conj:winfty-stage4-ward-inheritance}.
\end{remark}

\begin{proposition}[Stage-\texorpdfstring{$4$}{4} visible mixed-weight orthogonality from
the Virasoro Ward identity; \ClaimStatusProvedHere]
\label{prop:winfty-stage4-visible-orthogonality}
Let $\mathcal{W}^{\mathrm{fact}}_\infty$ be a principal-stage
compatible factorization target in the sense of
Proposition~\ref{prop:winfty-factorization-package}, and let
$\mathcal{F}_{\le 4}$ be its stage-$4$ quotient.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the visible generators $W^{(2)},W^{(3)},W^{(4)}$ in
  $\mathcal{F}_{\le 4}$ are even Virasoro-primary fields, and the local
  OPE is decomposed into their conformal families and translation
  descendants;
\item the Virasoro field $T:=W^{(2)}$ acts on these visible generators
  by the standard stage-$4$ Virasoro Ward identity;
\end{enumerate}
Then the quotient vacuum functional is mixed-weight orthogonal on the
visible generators:
\[
\langle W^{(s)}(z)W^{(t)}(0)\rangle = 0
\qquad (s\neq t,\ 2\le s,t\le 4).
\]
\end{proposition}

\begin{proof}
The global conformal Ward identities force
$\langle W^{(s)}(z)W^{(t)}(w)\rangle = C_{s,t}(z-w)^{-(s+t)}$;
the special conformal equation gives $(s-t)C_{s,t}=0$,
so $C_{s,t}=0$ whenever $s\neq t$.
\end{proof}

\begin{proposition}[Stage-\texorpdfstring{$4$}{4} visible
\texorpdfstring{$W^{(3)}$}{W3} normalization from the theorematic
\texorpdfstring{$W_3$}{W3} packet; \ClaimStatusProvedHere]
\label{prop:winfty-stage4-visible-w3-normalization}
Assume the hypotheses of
Proposition~\ref{prop:winfty-mc4-frontier-package}.  Assume moreover
that the stage-$4$ quotient residue calculus on the visible generators
$W^{(2)},W^{(3)},W^{(4)}$ is decomposed into conformal families of
Virasoro-primary generators and that the Virasoro field $T:=W^{(2)}$
acts on them, including on itself, by the standard stage-$4$
Virasoro Ward identity.  Then the visible stage-$4$ coefficient
\[
\mathsf{C}^{\mathrm{res}}_{3,3;2;0,4}(4)=2
\]
is already theorematic, and hence
\[
\langle W^{(3)}(z)W^{(3)}(0)\rangle=\frac{c/3}{z^{6}}.
\]
\end{proposition}

\begin{proof}
The tuple $(3,3,2,4)\in\mathcal{I}_4^{W_3}$ is fixed by the theorematic stage-$3$ packet (Proposition~\ref{prop:winfty-ds-stage3-explicit-packet}): $\mathsf{C}^{\mathrm{res}}_{3,3;2;0,4}(4)=2$.  Proposition~\ref{prop:winfty-formal-self-normalization-from-t} with $s=3$ then gives the displayed normalization.
\end{proof}

\begin{conjecture}[Stage-\texorpdfstring{$4$}{4} visible weight-\texorpdfstring{$4$}{4} normalization]
\label{conj:winfty-stage4-visible-diagonal-normalization}
\ClaimStatusConjectured{}
Let $\mathcal{W}^{\mathrm{fact}}_\infty$ be a principal-stage
compatible factorization target in the sense of
Proposition~\ref{prop:winfty-factorization-package}, and let
$\mathcal{F}_{\le 4}$ be its stage-$4$ quotient.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the visible generators $W^{(2)},W^{(3)},W^{(4)}$ in
  $\mathcal{F}_{\le 4}$ are even Virasoro-primary fields, and the local
  OPE is decomposed into their conformal families and translation
  descendants;
\item the Virasoro field $T:=W^{(2)}$ acts on these visible generators
  by the standard stage-$4$ Virasoro Ward identity, including on
  itself.
\end{enumerate}
Then the remaining visible self-pairing is normalized by
\[
\langle W^{(4)}(z)W^{(4)}(0)\rangle = \frac{c/4}{z^{8}}
\]
with the same nonzero central charge $c$ as on the principal
Drinfeld--Sokolov stage.  Equivalently,
\[
\mathsf{C}^{\mathrm{res}}_{4,4;2;0,6}(4)=2.
\]
\end{conjecture}

\begin{conjecture}[Automatic stage-\texorpdfstring{$4$}{4} Ward normalization from the
visible Virasoro package]
\label{conj:winfty-stage4-ward-inheritance}
\ClaimStatusConjectured{}
Let $\mathcal{W}^{\mathrm{fact}}_\infty$ be a principal-stage
compatible factorization target in the sense of
Proposition~\ref{prop:winfty-factorization-package}, and let
$\mathcal{F}_{\le 4}$ be its stage-$4$ quotient.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the visible generators $W^{(2)},W^{(3)},W^{(4)}$ in
  $\mathcal{F}_{\le 4}$ are even Virasoro-primary fields, and the local
  OPE is decomposed into their conformal families and translation
  descendants;
\item the Virasoro field $T:=W^{(2)}$ acts on these visible generators
  by the standard stage-$4$ Virasoro Ward identity, including on
  itself;
\end{enumerate}
Then the induced H-level target is stage-$4$ Ward-normalized in the
sense of Definition~\ref{def:winfty-stage4-ward-normalized}.  Consequently
Corollary~\ref{cor:winfty-stage4-residue-four-channel} applies, so the
first live standard-tower stage-$4$ packet contracts from the
unconditional six-entry block of
Proposition~\ref{prop:winfty-mc4-frontier-package} to the four
higher-spin channels
\[
(3,3;4;0,2),\qquad
(4,4;4;0,4),\qquad
(3,4;3;0,4),\qquad
(3,4;4;0,3).
\]
\end{conjecture}

\begin{corollary}[Equivalent exact forms of the remaining
\texorpdfstring{$W_\infty$}{W_infty} stage-\texorpdfstring{$4$}{4} input;
\ClaimStatusProvedHere]
\label{cor:winfty-stage4-single-scalar-equivalent}
Assume the hypotheses of
Proposition~\ref{prop:winfty-mc4-frontier-package}.  Assume moreover
that the stage-$4$ quotient residue calculus on the visible generators
$W^{(2)},W^{(3)},W^{(4)}$ is decomposed into conformal families of
Virasoro-primary generators and that the Virasoro field $T:=W^{(2)}$
acts on these visible generators by the standard stage-$4$ Virasoro
Ward identity, including on itself.  Then the following are
equivalent:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the induced H-level target is stage-$4$ Ward-normalized in the
  sense of Definition~\ref{def:winfty-stage4-ward-normalized};
\item the visible weight-$4$ self-pairing is normalized by
  \[
  \langle W^{(4)}(z)W^{(4)}(0)\rangle = \frac{c/4}{z^{8}};
  \]
\item the single scalar residue identity
  \[
  \mathsf{C}^{\mathrm{res}}_{4,4;2;0,6}(4)=2
  \]
  holds.
\end{enumerate}
Under these equivalent conditions,
Corollary~\ref{cor:winfty-stage4-residue-four-channel} applies, so the
first live standard-tower stage-$4$ packet contracts from the
unconditional six-entry block to the four higher-spin channels
\[
(3,3;4;0,2),\qquad
(4,4;4;0,4),\qquad
(3,4;3;0,4),\qquad
(3,4;4;0,3).
\]
\end{corollary}

\begin{proof}
The equivalence \textup{(i)} \(\Longleftrightarrow\) \textup{(ii)} is
exactly Definition~\ref{def:winfty-stage4-ward-normalized}.  Under the
same visible Virasoro package,
Proposition~\ref{prop:winfty-formal-self-t-coefficient} with $s=4$
gives \textup{(ii)} \(\Longrightarrow\) \textup{(iii)}, and
Proposition~\ref{prop:winfty-formal-self-normalization-from-t} with
$s=4$ gives \textup{(iii)} \(\Longrightarrow\) \textup{(ii)}.
The final sentence is exactly
Corollary~\ref{cor:winfty-stage4-residue-four-channel}.
\end{proof}

\begin{proposition}[Stage-\texorpdfstring{$4$}{4} swap-even residue channel from a visible
invariant pairing; \ClaimStatusProvedHere]
\label{prop:winfty-stage4-residue-pairing-reduction}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage4-single-scalar-equivalent}.  Assume
moreover that the visible stage-$4$ quotient residue calculus carries a
bilinear pairing \((-, -)_{\mathrm{vis}}\) on the span of
\(W^{(2)},W^{(3)},W^{(4)}\) such that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the visible generators are pairwise orthogonal for distinct
  conformal weights, and the self-pairings are normalized by
  \[
  (W^{(2)},W^{(2)})_{\mathrm{vis}}=\frac{c}{2},\qquad
  (W^{(3)},W^{(3)})_{\mathrm{vis}}=\frac{c}{3},\qquad
  (W^{(4)},W^{(4)})_{\mathrm{vis}}=\frac{c}{4}
  \]
  with the same nonzero central charge~\(c\);
\item for the visible primary field \(W^{(3)}\), the pairing satisfies
  the standard primary invariant-pairing identity
  \[
  \bigl(W^{(3)}_{(1)}a,b\bigr)_{\mathrm{vis}}
  =
  -\bigl(a,W^{(3)}_{(3)}b\bigr)_{\mathrm{vis}}
  \]
  whenever \(a,b\) are visible generators.
\end{enumerate}
Then the swap-even residue channel is forced by the \((3,3)\)-block:
\[
\mathsf{C}^{\mathrm{res}}_{3,4;3;0,4}(4)
=
-\frac{3}{4}\,
\mathsf{C}^{\mathrm{res}}_{3,3;4;0,2}(4).
\]
Equivalently,
\[
\bigl(\mathsf{C}^{\mathrm{res}}_{3,4;3;0,4}(4)\bigr)^2
=
\frac{9}{16}\,
\bigl(\mathsf{C}^{\mathrm{res}}_{3,3;4;0,2}(4)\bigr)^2.
\]
\end{proposition}

\begin{proof}
Apply the $W^{(3)}$ invariant-pairing identity with $a=W^{(3)}$, $b=W^{(4)}$: mode $1$ produces $\mathsf{C}^{\mathrm{res}}_{3,3;4;0,2}\cdot c/4$, the complementary mode $3$ produces $\mathsf{C}^{\mathrm{res}}_{3,4;3;0,4}\cdot c/3$, and the sign is negative ($W^{(3)}$ odd weight).  Since $c\neq 0$, rearranging gives the displayed identity.
\end{proof}

\begin{corollary}[Stage-\texorpdfstring{$4$}{4} residue packet as three higher-spin
channels on the visible pairing locus; \ClaimStatusProvedHere]
\label{cor:winfty-stage4-residue-three-channel}
Assume the hypotheses of
Proposition~\ref{prop:winfty-stage4-residue-pairing-reduction}.  Then,
on the stage-$4$ Ward-normalized visible pairing locus, the first
genuinely open stage-$4$ higher-spin residue packet contracts from the
four-channel block of
Corollary~\ref{cor:winfty-stage4-residue-four-channel} to the
three-channel block
\[
\begin{gathered}
(3,3;4;0,2),\qquad
(4,4;4;0,4),\\
(3,4;4;0,3),
\end{gathered}
\]
with the swap-even channel \((3,4;3;0,4)\) recovered formally from
\((3,3;4;0,2)\) by
Proposition~\ref{prop:winfty-stage4-residue-pairing-reduction}.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:winfty-stage4-residue-pairing-reduction} forces $(3,4;3;0,4)$ from $(3,3;4;0,2)$; removing it leaves three channels.
\end{proof}

\begin{corollary}[Stage-\texorpdfstring{$4$}{4} higher-spin comparison as a
primitive-plus-transport square triple on the visible pairing locus;
\ClaimStatusProvedHere]
\label{cor:winfty-stage4-primitive-transport-square-triple}
Assume the hypotheses of
Proposition~\ref{prop:winfty-stage4-residue-pairing-reduction}.  Then,
on the stage-$4$ Ward-normalized visible pairing locus, the four
higher-spin identities of
Corollary~\ref{cor:winfty-stage4-residue-four-channel} are equivalent
at signless square-class level to the three identities
\[
\bigl(\mathsf{C}^{\mathrm{res}}_{3,3;4;0,2}(4)\bigr)^2
=
c_{334}^{\,2},
\qquad
\bigl(\mathsf{C}^{\mathrm{res}}_{4,4;4;0,4}(4)\bigr)^2
=
c_{444}^{\,2},
\]
\[
\bigl(\mathsf{C}^{\mathrm{res}}_{3,4;4;0,3}(4)\bigr)^2
=
\tfrac{5}{7}\,c_{334}^{\,2}.
\]
Equivalently, on that locus the swap-even square identity
\[
\bigl(\mathsf{C}^{\mathrm{res}}_{3,4;3;0,4}(4)\bigr)^2
=
\tfrac{9}{16}\,c_{334}^{\,2}
\]
is automatic once the \((3,3;4;0,2)\) square identity holds.  In
particular, the signless stage-$4$ higher-spin frontier on the visible
pairing locus consists of the two primitive self-coupling squares
\[
\bigl(\mathsf{C}^{\mathrm{res}}_{3,3;4;0,2}(4)\bigr)^2,
\qquad
\bigl(\mathsf{C}^{\mathrm{res}}_{4,4;4;0,4}(4)\bigr)^2
\]
together with the swap-odd \(W^{(4)}\)-transport square
\[
\bigl(\mathsf{C}^{\mathrm{res}}_{3,4;4;0,3}(4)\bigr)^2.
\]
\end{corollary}

\begin{proof}
On the visible pairing locus, Proposition~\ref{prop:winfty-stage4-residue-pairing-reduction} gives
$(\mathsf{C}^{\mathrm{res}}_{3,4;3;0,4})^2 = \tfrac{9}{16}(\mathsf{C}^{\mathrm{res}}_{3,3;4;0,2})^2$.
On the principal side,
Corollary~\ref{cor:w4-ds-stage4-square-class-reduction} gives
\[
\mathsf{C}_{3,4;3;0,4}^{\,2}
=
\tfrac{9}{16}\,c_{334}^{\,2},
\qquad
\mathsf{C}_{3,4;4;0,3}^{\,2}
=
\tfrac{5}{7}\,c_{334}^{\,2}.
\]
Therefore the swap-even square identity is automatic once
\(
\bigl(\mathsf{C}^{\mathrm{res}}_{3,3;4;0,2}(4)\bigr)^2=c_{334}^{\,2}
\)
holds, while the remaining two displayed identities are exactly the
\((4,4)\) self-coupling square identity and the swap-odd
\(W^{(4)}\)-transport square identity.  The converse implication is
immediate.
\end{proof}

\begin{remark}[Exact next square-class gap after the visible pairing
reduction]
\label{rem:winfty-stage4-primitive-transport-gap}
Corollary~\ref{cor:winfty-stage4-primitive-transport-square-triple}
shows that the visible pairing package brings the residue side to the
same square-class profile as the principal side up to one additional
transport relation: the principal DS packet still forces
\[
\mathsf{C}_{3,4;4;0,3}^{\,2}
=
\tfrac{5}{7}\,c_{334}^{\,2},
\]
while on the residue side the corresponding relation
\[
\bigl(\mathsf{C}^{\mathrm{res}}_{3,4;4;0,3}(4)\bigr)^2
=
\tfrac{5}{7}\,
\bigl(\mathsf{C}^{\mathrm{res}}_{3,3;4;0,2}(4)\bigr)^2
\]
is not yet formal from the visible Ward plus pairing package alone.
Establishing this visible top-pole Borcherds transport relation would
reduce the residue higher-spin packet to the same two primitive
self-coupling square classes
\(
\bigl(\mathsf{C}^{\mathrm{res}}_{3,3;4;0,2}(4)\bigr)^2
\)
and
\(
\bigl(\mathsf{C}^{\mathrm{res}}_{4,4;4;0,4}(4)\bigr)^2
\)
as on the principal side.
\end{remark}

\begin{conjecture}[Stage-\texorpdfstring{$4$}{4} visible top-pole Borcherds transport]
\label{conj:winfty-stage4-visible-borcherds-transport}
\ClaimStatusConjectured{}
Assume the hypotheses of
Proposition~\ref{prop:winfty-stage4-residue-pairing-reduction}.  Then
the visible stage-$4$ quotient residue calculus satisfies the transport
square identity
\[
\bigl(\mathsf{C}^{\mathrm{res}}_{3,4;4;0,3}(4)\bigr)^2
=
\tfrac{5}{7}\,
\bigl(\mathsf{C}^{\mathrm{res}}_{3,3;4;0,2}(4)\bigr)^2.
\]
Equivalently, on the stage-$4$ Ward-normalized visible pairing locus
the swap-odd \(W^{(4)}\)-transport square is forced by the
\((3,3)\)-square.
\end{conjecture}

\begin{corollary}[Equivalent exact forms of the remaining stage-\texorpdfstring{$4$}{4}
higher-spin transport input on the visible pairing locus;
\ClaimStatusProvedHere]
\label{cor:winfty-stage4-visible-borcherds-two-primitive}
Assume the hypotheses of
Proposition~\ref{prop:winfty-stage4-residue-pairing-reduction}.  Then
the following are equivalent:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the visible top-pole Borcherds transport relation of
  Conjecture~\ref{conj:winfty-stage4-visible-borcherds-transport}
  holds:
  \[
  \bigl(\mathsf{C}^{\mathrm{res}}_{3,4;4;0,3}(4)\bigr)^2
  =
  \tfrac{5}{7}\,
  \bigl(\mathsf{C}^{\mathrm{res}}_{3,3;4;0,2}(4)\bigr)^2;
  \]
\item on the stage-$4$ Ward-normalized visible pairing locus, the
  higher-spin comparison of
  Corollary~\ref{cor:winfty-stage4-residue-four-channel} is equivalent
  at signless square-class level to the primitive pair
  \[
  \bigl(\mathsf{C}^{\mathrm{res}}_{3,3;4;0,2}(4)\bigr)^2
  =
  c_{334}^{\,2},
  \qquad
  \bigl(\mathsf{C}^{\mathrm{res}}_{4,4;4;0,4}(4)\bigr)^2
  =
  c_{444}^{\,2}.
  \]
\end{enumerate}
Under these equivalent conditions, the visible pairing locus has the
same two-primitive stage-$4$ square-class profile as the principal
Drinfeld--Sokolov side.
\end{corollary}

\begin{proof}
\textup{(i)}$\Rightarrow$\textup{(ii)}: the $\tfrac{5}{7}$-ratio from Corollary~\ref{cor:w4-ds-stage4-square-class-reduction} makes the transport square automatic once the $(3,3)$ primitive identity holds.  \textup{(ii)}$\Rightarrow$\textup{(i)}: the same principal formula recovers the transport relation.
\end{proof}

\begin{proposition}[Exact local attack order for the stage-\texorpdfstring{$4$}{4}
\texorpdfstring{$W_\infty$}{W_infty} packet; \ClaimStatusProvedHere]
\label{prop:winfty-stage4-local-attack-order}
Assume the hypotheses of
Proposition~\ref{prop:winfty-mc4-frontier-package}.  Assume moreover
that the stage-$4$ quotient residue calculus on the visible generators
\(W^{(2)},W^{(3)},W^{(4)}\) is decomposed into conformal families of
Virasoro-primary generators and that the Virasoro field \(T:=W^{(2)}\)
acts on them by the standard stage-$4$ Virasoro Ward identity,
including on itself.  Then the local stage-$4$ comparison separates
into two exact steps:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Virasoro-target normalization step.}
  The remaining input for the four-channel higher-spin refinement is
  exactly the visible weight-$4$ normalization, equivalently the single
  scalar identity
  \[
  \mathsf{C}^{\mathrm{res}}_{4,4;2;0,6}(4)=2;
  \]
\item \emph{Higher-spin transport step.}
  On the additional visible pairing locus of
  Proposition~\ref{prop:winfty-stage4-residue-pairing-reduction}, the
  remaining input for the principal two-primitive square profile is
  exactly the visible top-pole Borcherds transport relation
  \[
  \bigl(\mathsf{C}^{\mathrm{res}}_{3,4;4;0,3}(4)\bigr)^2
  =
  \tfrac{5}{7}\,
  \bigl(\mathsf{C}^{\mathrm{res}}_{3,3;4;0,2}(4)\bigr)^2.
  \]
\end{enumerate}
Equivalently, after the unconditional six-entry packet of
Proposition~\ref{prop:winfty-mc4-frontier-package}, the local
stage-$4$ frontier is first a one-scalar Ward-normalization problem and
then, on the visible pairing locus, a one-relation higher-spin
transport problem.
\end{proposition}

\begin{proof}
\textup{(i)}: Corollary~\ref{cor:winfty-stage4-single-scalar-equivalent}.  \textup{(ii)}: Corollary~\ref{cor:winfty-stage4-primitive-transport-square-triple} reduces to the primitive-plus-transport triple; Corollary~\ref{cor:winfty-stage4-visible-borcherds-two-primitive} closes it.
\end{proof}

\begin{remark}[Scope of the stage-4 Ward-inheritance conjecture]
The principal values are already explicit (Proposition~\ref{prop:w4-ds-ope-explicit}).  The open issue is whether the quotient-system hypotheses force the visible weight-$4$ normalization (Conjecture~\ref{conj:winfty-stage4-visible-diagonal-normalization}).  This is distinct from the higher-spin Borcherds transport gap (Conjecture~\ref{conj:winfty-stage4-visible-borcherds-transport}); if both are forced, the stage-$4$ comparison reduces to two primitive square classes (Corollary~\ref{cor:winfty-stage4-visible-borcherds-two-primitive}).
\end{remark}

\begin{proposition}[Uniform Virasoro-target contraction of reduced
incremental packets under the normalized residue package;
\ClaimStatusProvedHere]
\label{prop:winfty-stage-growth-virasoro-target-contraction}
Fix $N \ge 3$ and assume the hypotheses of
Corollary~\ref{cor:winfty-ds-stage-growth-top-parity}.  Assume
moreover that the stage-$(N+1)$ quotient residue calculus on the
visible generators
$W^{(2)},\dots,W^{(N+1)}$ satisfies the hypotheses of
Propositions~\ref{prop:winfty-formal-mixed-virasoro-zero}
and~\ref{prop:winfty-formal-self-t-coefficient}.  Then the
Virasoro-target channels inside
$\mathcal{J}_{N+1}^{\mathrm{red}}$ are exactly
\[
\bigl\{
(s,N{+}1;2;0,s+N-1)\mid 3\le s\le N
\bigr\}
\sqcup
\bigl\{
(N{+}1,N{+}1;2;0,2N)
\bigr\}.
\]
Their residue values are theorematically fixed by
\[
\mathsf{C}^{\mathrm{res}}_{s,N+1;2;0,s+N-1}(N+1)=0
\qquad (3\le s\le N),
\]
\[
\mathsf{C}^{\mathrm{res}}_{N+1,N+1;2;0,2N}(N+1)=2.
\]
Consequently the reduced incremental packet contracts to the
higher-spin packet
\[
\mathcal{J}_{N+1}^{\mathrm{hs}}
:=
\mathcal{J}_{N+1}^{\mathrm{red}}
\setminus
\Bigl(
\bigl\{
(s,N{+}1;2;0,s+N-1)\mid 3\le s\le N
\bigr\}
\sqcup
\bigl\{
(N{+}1,N{+}1;2;0,2N)
\bigr\}
\Bigr).
\]
For $N=3$ this recovers
Corollary~\ref{cor:winfty-stage4-residue-four-channel}.
\end{proposition}

\begin{proof}
Proposition~\ref{prop:winfty-formal-mixed-virasoro-zero} kills each mixed target-$2$ channel $(s,N{+}1;2;0,s+N-1)$; Proposition~\ref{prop:winfty-formal-self-t-coefficient} fixes the self target-$2$ channel to $2$.  Removing these leaves $\mathcal{J}_{N+1}^{\mathrm{hs}}$.
\end{proof}

\begin{corollary}[First reduced stage beyond
\texorpdfstring{$\mathcal{I}_4$}{I4} under the normalized residue
package; \ClaimStatusProvedHere]
\label{cor:winfty-stage5-residue-eight-channel}
Assume the hypotheses of
Corollary~\ref{cor:winfty-ds-stage5-reduced-packet}.  Assume moreover
that the stage-$5$ quotient residue calculus on the visible generators
$W^{(2)},W^{(3)},W^{(4)},W^{(5)}$ satisfies the hypotheses of
Propositions~\ref{prop:winfty-formal-mixed-virasoro-zero}
and~\ref{prop:winfty-formal-self-t-coefficient}.  Then the three
Virasoro-target channels in $\mathcal{J}_5^{\mathrm{red}}$ are
theorematically fixed:
\[
\mathsf{C}^{\mathrm{res}}_{3,5;2;0,6}(5)=0,
\qquad
\mathsf{C}^{\mathrm{res}}_{4,5;2;0,7}(5)=0,
\qquad
\mathsf{C}^{\mathrm{res}}_{5,5;2;0,8}(5)=2.
\]
Consequently the first reduced stage beyond~$\mathcal{I}_4$ contracts
to the eight higher-spin channels
\[
\begin{gathered}
(3,4;5;0,2),\\
(3,5;3;0,5),\qquad
(3,5;4;0,4),\qquad
(3,5;5;0,3),\\
(4,5;3;0,6),\qquad
(4,5;4;0,5),\qquad
(4,5;5;0,4),\\
(5,5;4;0,6).
\end{gathered}
\]
\end{corollary}

\begin{proof}
Apply
Proposition~\ref{prop:winfty-stage-growth-virasoro-target-contraction}
with $N=4$, and use
Corollary~\ref{cor:winfty-ds-stage5-reduced-packet} to identify the
resulting packet explicitly.
\end{proof}

\begin{corollary}[First higher-spin packet beyond
\texorpdfstring{$\mathcal{I}_4$}{I4}; \ClaimStatusProvedHere]
\label{cor:winfty-stage5-higher-spin-packet}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-residue-eight-channel}.  Then the
first higher-spin packet beyond the stage-$4$ four-channel block is
\[
\mathcal{J}_5^{\mathrm{hs}}
=
\Bigl\{
(3,4;5;0,2)
\Bigr\}
\sqcup
\Bigl\{
(3,5;3;0,5),\,
(3,5;4;0,4),\,
(3,5;5;0,3)
\Bigr\}
\]
\[
\sqcup
\Bigl\{
(4,5;3;0,6),\,
(4,5;4;0,5),\,
(4,5;5;0,4)
\Bigr\}
\sqcup
\Bigl\{
(5,5;4;0,6)
\Bigr\}.
\]
In particular,
\[
|\mathcal{J}_5^{\mathrm{hs}}|=8,
\]
and its block decomposition by source pair is
\[
1+3+3+1
\]
for the blocks
$(3,4)$, $(3,5)$, $(4,5)$, $(5,5)$.
\end{corollary}

\begin{proof}
Corollary~\ref{cor:winfty-stage5-residue-eight-channel} identifies the
contracted packet explicitly, and
Proposition~\ref{prop:winfty-stage-growth-virasoro-target-contraction}
defines that contracted packet to be
$\mathcal{J}_5^{\mathrm{hs}}$.
\end{proof}

\begin{remark}[Stage-$5$ higher-spin packet decomposition]
\label{prop:winfty-stage5-higher-spin-subblocks}%
\label{cor:winfty-stage5-entry-transport}%
\label{cor:winfty-stage5-entry-singletons}%
\label{prop:winfty-stage5-entry-mixed-self}%
\label{prop:winfty-stage5-reduced-tail-singleton}%
\label{prop:winfty-stage5-tail-mechanism}%
\label{prop:winfty-stage5-transport-target-ladders}%
\label{prop:winfty-stage5-higher-spin-target-blocks}%
\label{cor:winfty-stage5-target5-corridor}%
\label{cor:winfty-stage5-target5-residual}%
\label{prop:winfty-stage5-target5-transport-mechanism}%
\label{prop:winfty-stage5-target5-transport-singletons}%
\label{prop:winfty-stage5-transport-pole-profiles}%
\label{rem:winfty-stage5-first-subproblems}%
The $8$-element packet $\mathcal{J}_5^{\mathrm{hs}}$ of
Corollary~\ref{cor:winfty-stage5-higher-spin-packet} decomposes by
source pair into blocks $(3,4)$, $(3,5)$, $(4,5)$, $(5,5)$ of sizes
$1+3+3+1$.  The entry packet
$\mathcal{J}_5^{\mathrm{entry}}=\{(3,4;5;0,2),(5,5;4;0,6)\}$ carries
the mixed-entry singleton $\mathcal{J}_5^{\mathrm{ent,mix}}=\{(3,4;5;0,2)\}$ and the self-return
singleton $\mathcal{J}_5^{\mathrm{ent,self}}=\{(5,5;4;0,6)\}$; the transport packet
$\mathcal{J}_5^{\mathrm{tr}}$ has $6$ elements decomposing by target
spin into three $2$-element ladders $\mathcal{J}_5^{\mathrm{tr},u}$ for
$u=3,4,5$.  By target spin,
$\mathcal{J}_5^{u=3}$, $\mathcal{J}_5^{u=4}$, $\mathcal{J}_5^{u=5}$
have sizes $2,3,3$.  The target-$5$ corridor
$\mathcal{J}_5^{u=5}=\{(3,4;5;0,2),(3,5;5;0,3),(4,5;5;0,4)\}$ sits at
consecutive pole orders $2,3,4$; its residual continuation after the
tail singleton consists of the two transport singletons
$(3,5;5;0,3)$ and $(4,5;5;0,4)$, representing the
$W^{(5)}$-projection coefficients
$\mathsf{C}^{\mathrm{res}}_{3,5;5;0,3}(5)$ and
$\mathsf{C}^{\mathrm{res}}_{4,5;5;0,4}(5)$.  The reduced tail block
$\mathcal{J}_5^{\mathrm{tail,red}}=\{(3,4;5;0,2)\}$ identifies the
missing mechanism as matching
$\mathsf{C}^{\mathrm{res}}_{3,4;5;0,2}(5)=\mathsf{C}^{\mathrm{DS}}_{3,4;5;0,2}(5)$.
Transport ladders have pole profiles $\{3,4\}$, $\{4,5\}$, $\{5,6\}$
for targets $5,4,3$ respectively.
\end{remark}

\begin{proposition}[Stage-\texorpdfstring{$5$}{5} visible
\texorpdfstring{$W^{(5)}$}{W5} normalization from the theorematic
\texorpdfstring{$W^{(5)}$-$W^{(5)}\to T$}{W5-W5 to T} coefficient;
\ClaimStatusProvedHere]
\label{prop:winfty-stage5-visible-w5-normalization}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-residue-eight-channel}.  Assume
moreover that the stage-$5$ quotient residue calculus on the visible
generators $W^{(2)},W^{(3)},W^{(4)},W^{(5)}$ is decomposed into
conformal families of Virasoro-primary generators and that the
Virasoro field $T:=W^{(2)}$ acts on them, including on itself, by the
standard stage-$5$ Virasoro Ward identity.  Then the visible stage-$5$
coefficient
\[
\mathsf{C}^{\mathrm{res}}_{5,5;2;0,8}(5)=2
\]
is already theorematic, and hence
\[
\langle W^{(5)}(z)W^{(5)}(0)\rangle=\frac{c/5}{z^{10}}.
\]
\end{proposition}

\begin{proof}
Apply Proposition~\ref{prop:winfty-formal-self-normalization-from-t} with $s=5$.
\end{proof}

\begin{proposition}[Stage-\texorpdfstring{$5$}{5} target-\texorpdfstring{$5$}{5} pole-\texorpdfstring{$3$}{3} transport singleton
vanishes on a visible \texorpdfstring{$W^{(5)}$}{W5}-pairing locus;
\ClaimStatusProvedHere]
\label{prop:winfty-stage5-target5-pole3-pairing-vanishing}
Assume the hypotheses of
Proposition~\ref{prop:winfty-stage5-target5-transport-singletons}.
Assume moreover that the visible stage-$5$ quotient residue calculus
carries a bilinear pairing \((-, -)_{\mathrm{vis}}\) on the span of
\(W^{(2)},W^{(3)},W^{(4)},W^{(5)}\) such that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the visible generators are even Virasoro-primary fields,
  pairwise orthogonal for distinct conformal weights, and their
  self-pairings are normalized by
  \[
  (W^{(u)},W^{(u)})_{\mathrm{vis}}=\frac{c}{u}
  \qquad (2\le u\le 5)
  \]
  with the same nonzero central charge \(c\);
\item for the visible primary field \(W^{(5)}\), the pairing satisfies
  the standard primary invariant-pairing identity
  \[
  \bigl(W^{(5)}_{(n)}a,b\bigr)_{\mathrm{vis}}
  =
  -\bigl(a,W^{(5)}_{(8-n)}b\bigr)_{\mathrm{vis}}
  \]
  whenever \(a,b\) are visible generators and the displayed modes are
  defined.
\end{enumerate}
Then the first singleton in the residual target-$5$ continuation
vanishes:
\[
\mathsf{C}^{\mathrm{res}}_{3,5;5;0,3}(5)=0.
\]
\end{proposition}

\begin{proof}
The invariant-pairing identity of assumption~\textup{(ii)} with \(n=2\), \(a=W^{(3)}\), \(b=W^{(5)}\) relates the reversed-order coefficient \(\mathsf{C}^{\mathrm{res}}_{5,3;5;0,3}=-\mathsf{C}^{\mathrm{res}}_{3,5;5;0,3}\) (swap parity, \(3+5-5=3\) odd, by Proposition~\ref{prop:winfty-ds-mixed-top-pole-swap}) to the complementary mode \(8-2=6\) self-OPE coefficient \((5,5;3;0,7)\), which vanishes by Proposition~\ref{prop:winfty-ds-self-ope-parity} (odd self-OPE).  Since \(c\neq 0\), the displayed vanishing follows.
\end{proof}

\begin{proposition}[Stage-\texorpdfstring{$5$}{5} target-\texorpdfstring{$5$}{5} pole-\texorpdfstring{$4$}{4} transport singleton
from the self-return singleton on a visible
\texorpdfstring{$W^{(5)}$}{W5}-pairing locus; \ClaimStatusProvedHere]
\label{prop:winfty-stage5-target5-pole4-from-self-return}
Assume the hypotheses of
Proposition~\ref{prop:winfty-stage5-target5-transport-singletons} and
Proposition~\ref{prop:winfty-stage5-target5-pole3-pairing-vanishing}.
Then
\[
\mathsf{C}^{\mathrm{res}}_{4,5;5;0,4}(5)
=
-\frac{5}{4}\,
\mathsf{C}^{\mathrm{res}}_{5,5;4;0,6}(5).
\]
\end{proposition}

\begin{proof}
Apply the invariant-pairing technique of Proposition~\ref{prop:winfty-stage5-target5-pole3-pairing-vanishing} with \(n=3\), \(a=W^{(4)}\), \(b=W^{(5)}\).  The swap symmetry of Proposition~\ref{prop:winfty-ds-mixed-top-pole-swap} (\(4+5-5=4\) even) gives \(\mathsf{C}^{\mathrm{res}}_{5,4;5;0,4}=\mathsf{C}^{\mathrm{res}}_{4,5;5;0,4}\); the complementary mode \(8-3=5\) produces \(\mathsf{C}^{\mathrm{res}}_{5,5;4;0,6}\); the sign is negative (\(W^{(5)}\) odd weight).  Weight orthogonality and \(c\neq 0\) yield the displayed identity.
\end{proof}

\begin{proposition}[Stage-\texorpdfstring{$5$}{5} target-\texorpdfstring{$5$}{5} pole-\texorpdfstring{$4$}{4} transport singleton
vanishes on a visible \texorpdfstring{$W^{(4)}$}{W4}-pairing locus;
\ClaimStatusProvedHere]
\label{prop:winfty-stage5-target5-pole4-w4-vanishing}
Assume the hypotheses of
Proposition~\ref{prop:winfty-stage5-target5-transport-singletons}.
Assume moreover that the visible stage-$5$ quotient residue calculus
carries a bilinear pairing \((-, -)_{\mathrm{vis}}\) on the span of
\(W^{(2)},W^{(3)},W^{(4)},W^{(5)}\) such that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the visible generators are even Virasoro-primary fields,
  pairwise orthogonal for distinct conformal weights, and their
  self-pairings are normalized by
  \[
  (W^{(u)},W^{(u)})_{\mathrm{vis}}=\frac{c}{u}
  \qquad (2\le u\le 5)
  \]
  with the same nonzero central charge \(c\);
\item for the visible primary field \(W^{(4)}\), the pairing satisfies
  the standard primary invariant-pairing identity
  \[
  \bigl(W^{(4)}_{(n)}a,b\bigr)_{\mathrm{vis}}
  =
  \bigl(a,W^{(4)}_{(6-n)}b\bigr)_{\mathrm{vis}}
  \]
  whenever \(a,b\) are visible generators and the displayed modes are
  defined.
\end{enumerate}
Then
\[
\mathsf{C}^{\mathrm{res}}_{4,5;5;0,4}(5)=0.
\]
\end{proposition}

\begin{proof}
The invariant-pairing identity with \(n=3\), \(a=W^{(4)}\), \(b=W^{(5)}\) relates \(\mathsf{C}^{\mathrm{res}}_{4,4;5;0,3}\) (killed by odd self-OPE parity, Proposition~\ref{prop:winfty-ds-self-ope-parity}) to \(\mathsf{C}^{\mathrm{res}}_{4,5;5;0,4}\cdot c/4\).  Since \(c\neq 0\), the vanishing follows.
\end{proof}

\begin{corollary}[Stage-\texorpdfstring{$5$}{5} self-return singleton vanishes on the
visible \texorpdfstring{$W^{(4)}$}{W4}/\texorpdfstring{$W^{(5)}$}{W5}
pairing locus; \ClaimStatusProvedHere]
\label{cor:winfty-stage5-self-return-vanishing-on-pairing}
Assume the hypotheses of
Proposition~\ref{prop:winfty-stage5-target5-pole4-from-self-return}
and Proposition~\ref{prop:winfty-stage5-target5-pole4-w4-vanishing}.
Then
\[
\mathsf{C}^{\mathrm{res}}_{5,5;4;0,6}(5)=0.
\]
\end{corollary}

\begin{proof}
Combine Proposition~\ref{prop:winfty-stage5-target5-pole4-w4-vanishing} with
Proposition~\ref{prop:winfty-stage5-target5-pole4-from-self-return}.
\end{proof}

\begin{proposition}[Stage-\texorpdfstring{$5$}{5} reduced tail singleton from a visible
\texorpdfstring{$W^{(3)}$}{W3}-pairing locus; \ClaimStatusProvedHere]
\label{prop:winfty-stage5-tail-from-w3-pairing}
Under the hypotheses of
Proposition~\ref{prop:winfty-stage5-tail-mechanism}, assume moreover
the visible stage-$5$ pairing package of
Proposition~\ref{prop:winfty-stage5-target5-pole3-pairing-vanishing}
with the $W^{(3)}$ invariant-pairing identity
$\bigl(W^{(3)}_{(n)}a,b\bigr)_{\mathrm{vis}}
=-\bigl(a,W^{(3)}_{(4-n)}b\bigr)_{\mathrm{vis}}$.
Then:
\[
\mathsf{C}^{\mathrm{res}}_{3,4;5;0,2}(5)
=
-\frac{5}{4}\,
\mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}(5).
\]
\end{proposition}

\begin{proof}
Apply the $W^{(3)}$ invariant-pairing identity with \(n=1\), \(a=W^{(4)}\), \(b=W^{(5)}\); the complementary mode \(4-1=3\) produces \(\mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}\cdot c/4\).  The sign is negative (\(W^{(3)}\) odd weight).  Since \(c\neq 0\), rearranging gives the displayed identity.
\end{proof}

\begin{proposition}[Stage-\texorpdfstring{$5$}{5} reduced tail singleton from a visible
\texorpdfstring{$W^{(4)}$}{W4}-pairing locus; \ClaimStatusProvedHere]
\label{prop:winfty-stage5-tail-from-w4-pairing}
Under the hypotheses of
Proposition~\ref{prop:winfty-stage5-tail-mechanism}, assume the visible stage-$5$ pairing package of
Proposition~\ref{prop:winfty-stage5-target5-pole3-pairing-vanishing}
with the $W^{(4)}$ invariant-pairing identity
$\bigl(W^{(4)}_{(n)}a,b\bigr)_{\mathrm{vis}}
=\bigl(a,W^{(4)}_{(6-n)}b\bigr)_{\mathrm{vis}}$.
Then:
\[
\mathsf{C}^{\mathrm{res}}_{3,4;5;0,2}(5)
=
\frac{5}{3}\,
\mathsf{C}^{\mathrm{res}}_{4,5;3;0,6}(5).
\]
\end{proposition}

\begin{proof}
Apply the $W^{(4)}$ invariant-pairing identity with \(n=1\), \(a=W^{(3)}\), \(b=W^{(5)}\).  The swap symmetry of Proposition~\ref{prop:winfty-ds-mixed-top-pole-swap} (\(3+4-5=2\) even) gives \(\mathsf{C}^{\mathrm{res}}_{4,3;5;0,2}=\mathsf{C}^{\mathrm{res}}_{3,4;5;0,2}\); the complementary mode \(6-1=5\) produces \(\mathsf{C}^{\mathrm{res}}_{4,5;3;0,6}\cdot c/3\).  The sign is positive (\(W^{(4)}\) even weight).  Since \(c\neq 0\), rearranging gives the displayed identity.
\end{proof}

\begin{corollary}[Stage-\texorpdfstring{$5$}{5} tail singleton equates neighboring transport channels;
\ClaimStatusProvedHere]
\label{cor:winfty-stage5-tail-cross-target-reduction}
Under the hypotheses of
Propositions~\ref{prop:winfty-stage5-tail-from-w3-pairing}
and~\ref{prop:winfty-stage5-tail-from-w4-pairing}:
$\mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}(5)
=
-\frac{4}{3}\,
\mathsf{C}^{\mathrm{res}}_{4,5;3;0,6}(5)$.
\end{corollary}

\begin{proof}
Eliminate \(\mathsf{C}^{\mathrm{res}}_{3,4;5;0,2}(5)\) between the two propositions.
\end{proof}

\begin{corollary}[Stage-\texorpdfstring{$5$}{5} target-\texorpdfstring{$5$}{5} corridor contracts to the tail
singleton; \ClaimStatusProvedHere]
\label{cor:winfty-stage5-target5-corridor-to-tail}
Under the hypotheses of
Propositions~\ref{prop:winfty-stage5-target5-pole3-pairing-vanishing}
and~\ref{prop:winfty-stage5-target5-pole4-w4-vanishing}:
$\mathsf{C}^{\mathrm{res}}_{3,5;5;0,3}(5)=0$ and
$\mathsf{C}^{\mathrm{res}}_{4,5;5;0,4}(5)=0$.
\end{corollary}

\begin{corollary}[Stage-\texorpdfstring{$5$}{5} target-\texorpdfstring{$5$}{5} corridor carries no new
independent coefficient; \ClaimStatusProvedHere]
\label{cor:winfty-stage5-target5-no-new-independent-data}
Under the hypotheses of
Corollaries~\ref{cor:winfty-stage5-target5-corridor-to-tail}
and~\ref{cor:winfty-stage5-tail-cross-target-reduction}:
\[
\mathsf{C}^{\mathrm{res}}_{3,4;5;0,2}(5)
=
-\frac{5}{4}\,\mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}(5)
=
\frac{5}{3}\,\mathsf{C}^{\mathrm{res}}_{4,5;3;0,6}(5),
\]
while the two target-$5$ transport coefficients vanish.
\end{corollary}

\begin{proposition}[Stage-\texorpdfstring{$5$}{5} target-\texorpdfstring{$4$}{4} pole-\texorpdfstring{$5$}{5} transport singleton
vanishes; \ClaimStatusProvedHere]
\label{prop:winfty-stage5-target4-pole5-w4-vanishing}
Under the hypotheses of
Proposition~\ref{prop:winfty-stage5-target5-pole4-w4-vanishing}:
$\mathsf{C}^{\mathrm{res}}_{4,5;4;0,5}(5)=0$.
\end{proposition}

\begin{proof}
The $W^{(4)}$ invariant-pairing identity with \(n=4\), \(a=W^{(5)}\), \(b=W^{(4)}\) relates \(\mathsf{C}^{\mathrm{res}}_{4,5;4;0,5}\cdot c/4\) to the complementary mode \(6-4=2\) self-OPE coefficient \((4,4;5;0,3)\), which vanishes by odd self-OPE parity (Proposition~\ref{prop:winfty-ds-self-ope-parity}).
\end{proof}

\begin{proposition}[Stage-\texorpdfstring{$5$}{5} target-\texorpdfstring{$3$}{3} pole-\texorpdfstring{$5$}{5} transport singleton
vanishes; \ClaimStatusProvedHere]
\label{prop:winfty-stage5-target3-pole5-w3-vanishing}
Under the hypotheses of
Proposition~\ref{prop:winfty-stage5-tail-from-w3-pairing}:
$\mathsf{C}^{\mathrm{res}}_{3,5;3;0,5}(5)=0$.
\end{proposition}

\begin{proof}
The $W^{(3)}$ invariant-pairing identity with \(n=4\), \(a=W^{(5)}\), \(b=W^{(3)}\) relates \(\mathsf{C}^{\mathrm{res}}_{3,5;3;0,5}\cdot c/3\) to the complementary mode \(4-4=0\) self-OPE coefficient \((3,3;5;0,1)\), which vanishes by odd self-OPE parity (Proposition~\ref{prop:winfty-ds-self-ope-parity}).
\end{proof}

\begin{proposition}[Stage-\texorpdfstring{$5$}{5} target-\texorpdfstring{$4$}{4}/target-\texorpdfstring{$3$}{3} transport channels
are paired on a visible \texorpdfstring{$W^{(5)}$}{W5}-pairing locus;
\ClaimStatusProvedHere]
\label{prop:winfty-stage5-transport-cross-target-reduction}
Assume the hypotheses of
Proposition~\ref{prop:winfty-stage5-target5-pole3-pairing-vanishing}.
Then
\[
\mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}(5)
=
-\frac{4}{3}\,
\mathsf{C}^{\mathrm{res}}_{4,5;3;0,6}(5).
\]
\end{proposition}

\begin{proof}
Apply the $W^{(5)}$ invariant-pairing identity with \(n=3\), \(a=W^{(3)}\), \(b=W^{(4)}\).  The swap symmetry of Proposition~\ref{prop:winfty-ds-mixed-top-pole-swap} gives \(\mathsf{C}^{\mathrm{res}}_{5,3;4;0,4}=\mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}\) (\(3+5-4=4\) even) and \(\mathsf{C}^{\mathrm{res}}_{5,4;3;0,6}=\mathsf{C}^{\mathrm{res}}_{4,5;3;0,6}\) (\(4+5-3=6\) even).  The sign is negative (\(W^{(5)}\) odd weight).  Weight orthogonality and \(c\neq 0\) yield the displayed identity.
\end{proof}

\begin{corollary}[Stage-\texorpdfstring{$5$}{5} mixed transport frontier carries one
effective independent coefficient; \ClaimStatusProvedHere]
\label{cor:winfty-stage5-transport-effective-independent-frontier}
Under the hypotheses of
Propositions~\ref{prop:winfty-stage5-target4-pole5-w4-vanishing},
\ref{prop:winfty-stage5-target3-pole5-w3-vanishing}, and
\ref{prop:winfty-stage5-transport-cross-target-reduction}:
$\mathsf{C}^{\mathrm{res}}_{4,5;4;0,5}(5)=0$,
$\mathsf{C}^{\mathrm{res}}_{3,5;3;0,5}(5)=0$, and
$\mathsf{C}^{\mathrm{res}}_{4,5;3;0,6}(5)
=
-\frac{3}{4}\,
\mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}(5)$.
\end{corollary}

\begin{corollary}[Stage-\texorpdfstring{$5$}{5} higher-spin packet reduces to one effective
independent coefficient; \ClaimStatusProvedHere]
\label{cor:winfty-stage5-effective-independent-frontier}
Under the hypotheses of
Corollaries~\ref{cor:winfty-stage5-self-return-vanishing-on-pairing},
\ref{cor:winfty-stage5-target5-no-new-independent-data}, and
\ref{cor:winfty-stage5-transport-effective-independent-frontier},
set $A_5:=\mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}(5)$.
Then every coefficient in $\mathcal{J}_5^{\mathrm{hs}}$ is either zero or determined by $A_5$:
\[
\mathsf{C}^{\mathrm{res}}_{3,4;5;0,2}(5)=-\tfrac{5}{4}\,A_5,
\quad
\mathsf{C}^{\mathrm{res}}_{4,5;3;0,6}(5)=-\tfrac{3}{4}\,A_5,
\]
with all other channels vanishing.
The effective independent coefficient is the target-$4$
singleton \((3,5;4;0,4)\).
\end{corollary}

\begin{proposition}[Exact local attack order for the first stage-\texorpdfstring{$5$}{5}
higher-spin packet; \ClaimStatusProvedHere]
\label{prop:winfty-stage5-local-attack-order}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-entry-transport}.  Then the first
stage-$5$ higher-spin frontier separates into the following exact local
order:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Entry step.}  The attack begins with the two-channel entry
  packet \(\mathcal{J}_5^{\mathrm{entry}}\), first through the
  mixed-entry singleton \((3,4;5;0,2)\) and then through the
  self-return singleton \((5,5;4;0,6)\).
\item \emph{Target-$5$ corridor step.}  The first local mixed-transport
  strip is the target-$5$ corridor
  \[
  (3,4;5;0,2),\qquad
  (3,5;5;0,3),\qquad
  (4,5;5;0,4),
  \]
  whose residual continuation after the tail singleton
  \((3,4;5;0,2)\) is exactly the two singleton transport ladder
  \[
  (3,5;5;0,3),\qquad
  (4,5;5;0,4),
  \]
  taken in pole order \(3\) then \(4\).
\item \emph{Remaining mixed transport step.}  After the target-$5$
  ladder, the remaining transport frontier is attacked by fixed target
  in the order
  \[
  \mathcal{J}_5^{\mathrm{tr},5},\qquad
  \mathcal{J}_5^{\mathrm{tr},4},\qquad
  \mathcal{J}_5^{\mathrm{tr},3}.
  \]
\end{enumerate}
On the visible pairing loci of
Propositions~\ref{prop:winfty-stage5-target5-pole3-pairing-vanishing}
--\ref{cor:winfty-stage5-tail-cross-target-reduction}, the same
target-$5$ corridor becomes more rigid: the pole-$3$ singleton
vanishes, the pole-$4$ singleton is tied to the self-return singleton,
and the tail singleton is tied to neighboring target-$4$/target-$3$
transport channels.  On the full visible
\texorpdfstring{$W^{(3)}$}{W3}/\texorpdfstring{$W^{(4)}$}{W4}/\texorpdfstring{$W^{(5)}$}{W5}
pairing locus of
Corollary~\ref{cor:winfty-stage5-target5-no-new-independent-data}, the
whole target-$5$ corridor carries no new independent coefficient, so
Proposition~\ref{prop:winfty-stage5-target4-pole5-w4-vanishing},
Proposition~\ref{prop:winfty-stage5-target3-pole5-w3-vanishing}, and
Proposition~\ref{prop:winfty-stage5-transport-cross-target-reduction}
collapse the remaining target-$4$/target-$3$ transport ladders to one
effective coefficient, and
Corollary~\ref{cor:winfty-stage5-effective-independent-frontier}
identifies the effective independent local attack order there as the
single target-$4$ singleton \((3,5;4;0,4)\), with every other stage-$5$
higher-spin channel either zero or determined by it.
\end{proposition}

\begin{proof}
Parts \textup{(i)}--\textup{(iii)} follow from the packet decompositions already established:
Corollary~\ref{cor:winfty-stage5-entry-transport} for the entry/transport split,
Corollary~\ref{cor:winfty-stage5-target5-corridor} for the target-$5$ corridor,
and Proposition~\ref{prop:winfty-stage5-transport-pole-profiles} for the transport ladder ordering.
The visible-pairing refinement combines
Propositions~\ref{prop:winfty-stage5-target5-pole3-pairing-vanishing}--\ref{prop:winfty-stage5-transport-cross-target-reduction}
with Corollary~\ref{cor:winfty-stage5-effective-independent-frontier}.
\end{proof}

\begin{conjecture}[Principal stage-\texorpdfstring{$5$}{5} target-\texorpdfstring{$5$}{5} corridor carries no
new independent coefficient on the full visible pairing locus]
\label{conj:winfty-stage5-principal-target5-no-new-independent-data}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-effective-independent-frontier}.  Then
\[
\mathsf{C}^{\mathrm{DS}}_{3,4;5;0,2}(5)
=
-\frac{5}{4}\,\mathsf{C}^{\mathrm{DS}}_{3,5;4;0,4}(5)
=
\frac{5}{3}\,\mathsf{C}^{\mathrm{DS}}_{4,5;3;0,6}(5),
\]
\[
\mathsf{C}^{\mathrm{DS}}_{3,5;5;0,3}(5)=0,
\qquad
\mathsf{C}^{\mathrm{DS}}_{4,5;5;0,4}(5)=0.
\]
Equivalently, on the full visible
\texorpdfstring{$W^{(3)}$}{W3}/\texorpdfstring{$W^{(4)}$}{W4}/\texorpdfstring{$W^{(5)}$}{W5}
pairing locus the principal target-$5$ corridor carries no new
independent coefficient beyond the neighboring target-$4$/target-$3$
channels.
\end{conjecture}

\begin{conjecture}[Principal stage-\texorpdfstring{$5$}{5} target-\texorpdfstring{$5$}{5} transport channels
vanish on the full visible pairing locus]
\label{conj:winfty-stage5-principal-target5-transport-vanishing}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-effective-independent-frontier}.  Then
\[
\mathsf{C}^{\mathrm{DS}}_{3,5;5;0,3}(5)=0,
\qquad
\mathsf{C}^{\mathrm{DS}}_{4,5;5;0,4}(5)=0.
\]
Equivalently, on the full visible
\texorpdfstring{$W^{(3)}$}{W3}/\texorpdfstring{$W^{(4)}$}{W4}/\texorpdfstring{$W^{(5)}$}{W5}
pairing locus the principal target-$5$ corridor contracts to the tail
singleton.
\end{conjecture}

\begin{conjecture}[Principal stage-\texorpdfstring{$5$}{5} tail singleton is tied to the
neighboring target-\texorpdfstring{$4$}{4}/target-\texorpdfstring{$3$}{3} channels on the full visible pairing locus]
\label{conj:winfty-stage5-principal-tail-cross-target-reduction}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-effective-independent-frontier}.  Then
\[
\mathsf{C}^{\mathrm{DS}}_{3,4;5;0,2}(5)
=
-\frac{5}{4}\,\mathsf{C}^{\mathrm{DS}}_{3,5;4;0,4}(5)
=
\frac{5}{3}\,\mathsf{C}^{\mathrm{DS}}_{4,5;3;0,6}(5).
\]
Equivalently, on the full visible pairing locus the principal reduced
tail singleton adds no new independent coefficient beyond the
neighboring target-$4$/target-$3$ transport channels.
\end{conjecture}

\begin{remark}[Target-$5$ corridor factorization]
\label{prop:winfty-stage5-principal-target5-factorization}%
Conjecture~\ref{conj:winfty-stage5-principal-target5-no-new-independent-data}
holds if and only if both
Conjecture~\ref{conj:winfty-stage5-principal-target5-transport-vanishing}
and
Conjecture~\ref{conj:winfty-stage5-principal-tail-cross-target-reduction}
hold: the two transport vanishings together with the tail cross-target relation account for all five identities.
\end{remark}

\begin{conjecture}[Principal residual stage-\texorpdfstring{$5$}{5} front carries one
effective independent coefficient on the full visible pairing locus]
\label{conj:winfty-stage5-principal-residual-front-one-coefficient}%
\label{conj:winfty-stage5-principal-residual-front-vanishings}%
\label{conj:winfty-stage5-principal-residual-cross-target-reduction}%
\label{prop:winfty-stage5-principal-residual-front-factorization}%
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-effective-independent-frontier}.  Then
\[
\mathsf{C}^{\mathrm{DS}}_{5,5;4;0,6}(5)=0,
\qquad
\mathsf{C}^{\mathrm{DS}}_{4,5;4;0,5}(5)=0,
\qquad
\mathsf{C}^{\mathrm{DS}}_{3,5;3;0,5}(5)=0,
\]
\[
\mathsf{C}^{\mathrm{DS}}_{4,5;3;0,6}(5)
=
-\frac{3}{4}\,\mathsf{C}^{\mathrm{DS}}_{3,5;4;0,4}(5).
\]
Equivalently, outside the target-$5$ corridor, the principal stage-$5$
higher-spin packet carries one effective independent coefficient,
represented by the target-$4$ singleton \((3,5;4;0,4)\).
The three vanishings alone form the \emph{residual vanishing component}
and the cross-target relation
$\mathsf{C}^{\mathrm{DS}}_{4,5;3;0,6}(5)=-\tfrac{3}{4}\,\mathsf{C}^{\mathrm{DS}}_{3,5;4;0,4}(5)$
forms the \emph{residual cross-target reduction component};
the full conjecture holds if and only if both components hold.
\end{conjecture}

\begin{conjecture}[Principal stage-\texorpdfstring{$5$}{5} one-coefficient normal form on the
full visible pairing locus]
\label{conj:winfty-stage5-principal-one-coefficient-normal-form}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-effective-independent-frontier}.  Then
the principal stage-$5$ target packet satisfies the same one-coefficient
normal form:
\[
\mathsf{C}^{\mathrm{DS}}_{3,4;5;0,2}(5)
=
-\frac{5}{4}\,\mathsf{C}^{\mathrm{DS}}_{3,5;4;0,4}(5),
\qquad
\mathsf{C}^{\mathrm{DS}}_{3,5;5;0,3}(5)=0,
\qquad
\mathsf{C}^{\mathrm{DS}}_{4,5;5;0,4}(5)=0,
\]
\[
\mathsf{C}^{\mathrm{DS}}_{5,5;4;0,6}(5)=0,
\qquad
\mathsf{C}^{\mathrm{DS}}_{4,5;4;0,5}(5)=0,
\qquad
\mathsf{C}^{\mathrm{DS}}_{3,5;3;0,5}(5)=0,
\qquad
\mathsf{C}^{\mathrm{DS}}_{4,5;3;0,6}(5)
=
-\frac{3}{4}\,\mathsf{C}^{\mathrm{DS}}_{3,5;4;0,4}(5).
\]
Equivalently, on the full visible
\texorpdfstring{$W^{(3)}$}{W3}/\texorpdfstring{$W^{(4)}$}{W4}/\texorpdfstring{$W^{(5)}$}{W5}
pairing locus the principal stage-$5$ higher-spin packet carries one
effective independent coefficient, represented by the target-$4$
singleton \((3,5;4;0,4)\).  Equivalently again, this is the conjunction
of
Conjectures~\ref{conj:winfty-stage5-principal-target5-no-new-independent-data}
and~\ref{conj:winfty-stage5-principal-residual-front-one-coefficient}.
\end{conjecture}

\begin{proposition}[Principal stage-\texorpdfstring{$5$}{5} one-coefficient normal form
factors through the target-\texorpdfstring{$5$}{5} corridor and the residual front;
\ClaimStatusProvedHere]
\label{prop:winfty-stage5-principal-one-coefficient-factorization}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-effective-independent-frontier}.  Then
Conjecture~\ref{conj:winfty-stage5-principal-one-coefficient-normal-form}
holds if and only if both
Conjecture~\ref{conj:winfty-stage5-principal-target5-no-new-independent-data}
and
Conjecture~\ref{conj:winfty-stage5-principal-residual-front-one-coefficient}
hold.
\end{proposition}

\begin{proof}
Combine Propositions~\ref{prop:winfty-stage5-principal-target5-factorization} and~\ref{prop:winfty-stage5-principal-residual-front-factorization}; together they account for all seven identities in the normal form.
\end{proof}

\begin{proposition}[Stage-\texorpdfstring{$5$}{5} higher-spin comparison reduces to one
coefficient on the full visible pairing locus; \ClaimStatusProvedHere]
\label{prop:winfty-stage5-one-coefficient-reduction}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-effective-independent-frontier} and
Conjecture~\ref{conj:winfty-stage5-principal-one-coefficient-normal-form}.
Then the full stage-$5$ higher-spin comparison on
\(\mathcal{J}_5^{\mathrm{hs}}\) is equivalent to the single identity of
Conjecture~\ref{conj:winfty-stage5-one-coefficient-comparison},
\[
\mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}(5)
=
\mathsf{C}^{\mathrm{DS}}_{3,5;4;0,4}(5).
\]
\end{proposition}

\begin{proof}
Corollary~\ref{cor:winfty-stage5-effective-independent-frontier} expresses every residue coefficient as a fixed multiple of \(\mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}(5)\); matching this singleton matches all channels.
\end{proof}

\begin{conjecture}[Stage-\texorpdfstring{$5$}{5} one-coefficient comparison on the full
visible pairing locus]
\label{conj:winfty-stage5-one-coefficient-comparison}
\ClaimStatusConjectured{}
Assume the hypotheses of
Proposition~\ref{prop:winfty-stage5-one-coefficient-reduction}.  Then
\[
\mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}(5)
=
\mathsf{C}^{\mathrm{DS}}_{3,5;4;0,4}(5).
\]
Equivalently, on the full visible
\texorpdfstring{$W^{(3)}$}{W3}/\texorpdfstring{$W^{(4)}$}{W4}/\texorpdfstring{$W^{(5)}$}{W5}
pairing locus the stage-$5$ higher-spin frontier closes once the
target-$4$ singleton \((3,5;4;0,4)\) is matched.
\end{conjecture}

\begin{corollary}[Exact remaining stage-\texorpdfstring{$5$}{5} visible-pairing input
package; \ClaimStatusProvedHere]
\label{cor:winfty-stage5-exact-remaining-input}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-effective-independent-frontier}.  Then
the full stage-$5$ higher-spin comparison on \(\mathcal{J}_5^{\mathrm{hs}}\)
closes on the full visible pairing locus if and only if the following
two inputs both hold:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the packaged principal one-coefficient normal form of
  Conjecture~\ref{conj:winfty-stage5-principal-one-coefficient-normal-form}
  holds;
\item the target-$4$ singleton identity
  \[
  \mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}(5)
  =
  \mathsf{C}^{\mathrm{DS}}_{3,5;4;0,4}(5)
  \]
  holds.
\end{enumerate}
Equivalently, the exact remaining local stage-$5$ visible-pairing
frontier is the packaged principal one-coefficient normal form together
with the singleton identity of
Conjecture~\ref{conj:winfty-stage5-one-coefficient-comparison}.  The
missing input is therefore no longer residue-side transport reduction,
but that packaged principal normal form together with that single
target-$4$ match.  Equivalently again, by
Proposition~\ref{prop:winfty-stage5-principal-one-coefficient-factorization},
this two-input package is the same as the pair of structural
conjectures
Conjectures~\ref{conj:winfty-stage5-principal-target5-no-new-independent-data}
and~\ref{conj:winfty-stage5-principal-residual-front-one-coefficient},
together with the singleton identity.
\end{corollary}

\begin{proof}
Necessity: the one-coefficient normal form of Corollary~\ref{cor:winfty-stage5-effective-independent-frontier} on the residue side forces the same on the principal side; the singleton identity is one matched channel.  Sufficiency: \textup{(i)} supplies the hypothesis of Proposition~\ref{prop:winfty-stage5-one-coefficient-reduction}, and \textup{(ii)} is the single identity to which it reduces.  The reformulation is Proposition~\ref{prop:winfty-stage5-principal-one-coefficient-factorization}.
\end{proof}

\begin{corollary}[Stage-\texorpdfstring{$5$}{5} higher-spin defect family collapses to one
representative defect on the full visible pairing locus;
\ClaimStatusProvedHere]
\label{cor:winfty-stage5-one-defect-family}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-effective-independent-frontier},
and
Conjecture~\ref{conj:winfty-stage5-principal-one-coefficient-normal-form}.
Set
\[
D_5:=
\mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}(5)
-
\mathsf{C}^{\mathrm{DS}}_{3,5;4;0,4}(5).
\]
Then every defect in the stage-$5$ higher-spin packet
\(\mathcal{J}_5^{\mathrm{hs}}\) is either zero or a fixed rational
multiple of \(D_5\).  Explicitly,
\[
\begin{aligned}
\mathsf{C}^{\mathrm{res}}_{3,4;5;0,2}(5)
-
\mathsf{C}^{\mathrm{DS}}_{3,4;5;0,2}(5)
&=
-\frac{5}{4}\,D_5,\\
\mathsf{C}^{\mathrm{res}}_{3,5;5;0,3}(5)
-
\mathsf{C}^{\mathrm{DS}}_{3,5;5;0,3}(5)
&=0,\\
\mathsf{C}^{\mathrm{res}}_{4,5;5;0,4}(5)
-
\mathsf{C}^{\mathrm{DS}}_{4,5;5;0,4}(5)
&=0,
\end{aligned}
\]
\[
\begin{aligned}
\mathsf{C}^{\mathrm{res}}_{5,5;4;0,6}(5)
-
\mathsf{C}^{\mathrm{DS}}_{5,5;4;0,6}(5)
&=0,\\
\mathsf{C}^{\mathrm{res}}_{4,5;4;0,5}(5)
-
\mathsf{C}^{\mathrm{DS}}_{4,5;4;0,5}(5)
&=0,\\
\mathsf{C}^{\mathrm{res}}_{3,5;3;0,5}(5)
-
\mathsf{C}^{\mathrm{DS}}_{3,5;3;0,5}(5)
&=0,
\end{aligned}
\]
\[
\mathsf{C}^{\mathrm{res}}_{4,5;3;0,6}(5)
-
\mathsf{C}^{\mathrm{DS}}_{4,5;3;0,6}(5)
=
-\frac{3}{4}\,D_5.
\]
Equivalently, on that full visible pairing locus the whole stage-$5$
higher-spin defect family on \(\mathcal{J}_5^{\mathrm{hs}}\) vanishes
if and only if \(D_5=0\).
\end{corollary}

\begin{proof}
Subtract the residue-side one-coefficient normal form from the principal-side normal form.
\end{proof}

\begin{conjecture}[Stage-\texorpdfstring{$5$}{5} entry-packet identities]
\label{conj:winfty-stage5-entry-identities}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-entry-transport}.  Then
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(5)
=
\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(5)
\]
for every channel $(s,t;u;m,n)$ in the two-channel packet
$\mathcal{J}_5^{\mathrm{entry}}$.  Equivalently, the singleton channel
conjectures
Conjectures~\ref{conj:winfty-stage5-block-34}
and~\ref{conj:winfty-stage5-block-55}
both hold, in the attack order dictated by
Proposition~\ref{prop:winfty-stage5-entry-mixed-self}.
\end{conjecture}

\begin{conjecture}[Stage-\texorpdfstring{$5$}{5} mixed transport identities]
\label{conj:winfty-stage5-transport-identities}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-entry-transport}.  Then
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(5)
=
\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(5)
\]
for every channel $(s,t;u;m,n)$ in the six-channel packet
$\mathcal{J}_5^{\mathrm{tr}}$.  Equivalently, the three fixed-target
ladder conjectures
Conjectures~\ref{conj:winfty-stage5-transport-target-3}
--\ref{conj:winfty-stage5-transport-target-5}
all hold.  By
Proposition~\ref{prop:winfty-stage5-transport-pole-profiles}, the
natural local attack order is target~$5$, then target~$4$, then
target~$3$.
\end{conjecture}

\begin{conjecture}[Stage-\texorpdfstring{$5$}{5} transport target-\texorpdfstring{$3$}{3} ladder identities]
\label{conj:winfty-stage5-transport-target-3}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-entry-transport}.  Then
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(5)
=
\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(5)
\]
for every channel $(s,t;u;m,n)$ in the two-channel ladder
$\mathcal{J}_5^{\mathrm{tr},3}$ of
Proposition~\ref{prop:winfty-stage5-transport-target-ladders}.
\end{conjecture}

\begin{conjecture}[Stage-\texorpdfstring{$5$}{5} transport target-\texorpdfstring{$4$}{4} ladder identities]
\label{conj:winfty-stage5-transport-target-4}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-entry-transport}.  Then
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(5)
=
\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(5)
\]
for every channel $(s,t;u;m,n)$ in the two-channel ladder
$\mathcal{J}_5^{\mathrm{tr},4}$ of
Proposition~\ref{prop:winfty-stage5-transport-target-ladders}.
\end{conjecture}

\begin{conjecture}[Stage-\texorpdfstring{$5$}{5} transport target-\texorpdfstring{$5$}{5} ladder identities]
\label{conj:winfty-stage5-transport-target-5}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-entry-transport}.  Then
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(5)
=
\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(5)
\]
for every channel $(s,t;u;m,n)$ in the two-channel ladder
$\mathcal{J}_5^{\mathrm{tr},5}$ of
Proposition~\ref{prop:winfty-stage5-transport-target-ladders}.  Together
with Conjecture~\ref{conj:winfty-stage5-block-34}, this matches every
channel in the target-$5$ corridor of
Corollary~\ref{cor:winfty-stage5-target5-corridor}; after the singleton
tail input of Proposition~\ref{prop:winfty-stage5-reduced-tail-singleton}
is matched, this is exactly the residual continuation identified in
Corollary~\ref{cor:winfty-stage5-target5-residual} and the mixed
transport mechanism identified in
Proposition~\ref{prop:winfty-stage5-target5-transport-mechanism}.
Equivalently, the two singleton transport conjectures
Conjectures~\ref{conj:winfty-stage5-transport-target5-35}
and~\ref{conj:winfty-stage5-transport-target5-45}
both hold, in the pole order dictated by
Proposition~\ref{prop:winfty-stage5-target5-transport-singletons}.
\end{conjecture}

\begin{conjecture}[Stage-\texorpdfstring{$5$}{5} target-\texorpdfstring{$5$}{5} transport singleton from
\texorpdfstring{$W^{(3)}W^{(5)}$}{W3W5}]
\label{conj:winfty-stage5-transport-target5-35}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-entry-transport}.  Then
\[
\mathsf{C}^{\mathrm{res}}_{3,5;5;0,3}(5)
=
\mathsf{C}^{\mathrm{DS}}_{3,5;5;0,3}(5).
\]
This is the first singleton in the residual target-$5$ continuation of
Proposition~\ref{prop:winfty-stage5-target5-transport-singletons},
equivalently the pole-$3$ $W^{(5)}$-projection in
$W^{(3)}(z)W^{(5)}(w)$.
\end{conjecture}

\begin{conjecture}[Stage-\texorpdfstring{$5$}{5} target-\texorpdfstring{$5$}{5} transport singleton from
\texorpdfstring{$W^{(4)}W^{(5)}$}{W4W5}]
\label{conj:winfty-stage5-transport-target5-45}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-entry-transport}.  Then
\[
\mathsf{C}^{\mathrm{res}}_{4,5;5;0,4}(5)
=
\mathsf{C}^{\mathrm{DS}}_{4,5;5;0,4}(5).
\]
This is the second singleton in the residual target-$5$ continuation of
Proposition~\ref{prop:winfty-stage5-target5-transport-singletons},
equivalently the pole-$4$ $W^{(5)}$-projection in
$W^{(4)}(z)W^{(5)}(w)$.
\end{conjecture}

\begin{conjecture}[Stage-\texorpdfstring{$5$}{5}
\texorpdfstring{$(3,4)$}{(3,4)} higher-spin block identity]
\label{conj:winfty-stage5-block-34}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-higher-spin-packet}.  Then
\[
\mathsf{C}^{\mathrm{res}}_{3,4;5;0,2}(5)
=
\mathsf{C}^{\mathrm{DS}}_{3,4;5;0,2}(5).
\]
This is exactly the reduced tail comparison input isolated in
Proposition~\ref{prop:winfty-stage5-reduced-tail-singleton}, the exact
missing comparison mechanism isolated in
Proposition~\ref{prop:winfty-stage5-tail-mechanism}, and the
first singleton channel in the target-$5$ corridor of
Corollary~\ref{cor:winfty-stage5-target5-corridor}.
\end{conjecture}

\begin{conjecture}[Stage-\texorpdfstring{$5$}{5}
\texorpdfstring{$(3,5)$}{(3,5)} higher-spin block identities]
\label{conj:winfty-stage5-block-35}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-higher-spin-packet}.  Then
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(5)
=
\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(5)
\]
for every channel $(s,t;u;m,n)$ in the three-channel block
$\mathcal{J}_5^{(3,5)}$ of
Proposition~\ref{prop:winfty-stage5-higher-spin-subblocks}.
\end{conjecture}

\begin{conjecture}[Stage-\texorpdfstring{$5$}{5}
\texorpdfstring{$(4,5)$}{(4,5)} higher-spin block identities]
\label{conj:winfty-stage5-block-45}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-higher-spin-packet}.  Then
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(5)
=
\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(5)
\]
for every channel $(s,t;u;m,n)$ in the three-channel block
$\mathcal{J}_5^{(4,5)}$ of
Proposition~\ref{prop:winfty-stage5-higher-spin-subblocks}.
\end{conjecture}

\begin{conjecture}[Stage-\texorpdfstring{$5$}{5}
\texorpdfstring{$(5,5)$}{(5,5)} self higher-spin block identity]
\label{conj:winfty-stage5-block-55}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-higher-spin-packet}.  Then
\[
\mathsf{C}^{\mathrm{res}}_{5,5;4;0,6}(5)
=
\mathsf{C}^{\mathrm{DS}}_{5,5;4;0,6}(5).
\]
\end{conjecture}

\begin{conjecture}[First higher-spin bar-vs-DS packet beyond
\texorpdfstring{$\mathcal{I}_4$}{I4}]
\label{conj:winfty-stage5-higher-spin-identities}
\ClaimStatusConjectured{}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-residue-eight-channel}.  Then
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(5)
=
\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(5)
\]
for every channel $(s,t;u;m,n)$ in the explicit packet
$\mathcal{J}_5^{\mathrm{hs}}$ of
Corollary~\ref{cor:winfty-stage5-higher-spin-packet}.  This is the
next finite list of higher-spin bar-vs-Drinfeld--Sokolov identities
after the stage-$4$ four-channel packet.  Equivalently, the four
subblock conjectures
Conjectures~\ref{conj:winfty-stage5-block-34}
--\ref{conj:winfty-stage5-block-55}
all hold, or, equivalently again, the entry-packet and mixed-transport
conjectures
Conjectures~\ref{conj:winfty-stage5-entry-identities}
and~\ref{conj:winfty-stage5-transport-identities}
both hold.  On the full visible
\texorpdfstring{$W^{(3)}$}{W3}/\texorpdfstring{$W^{(4)}$}{W4}/\texorpdfstring{$W^{(5)}$}{W5}
pairing locus,
Conjecture~\ref{conj:winfty-stage5-principal-one-coefficient-normal-form}
together with Proposition~\ref{prop:winfty-stage5-one-coefficient-reduction}
reduce this whole packet conjecture to the single scalar identity of
Conjecture~\ref{conj:winfty-stage5-one-coefficient-comparison},
and hence through the packaged principal one-coefficient normal form.
\end{conjecture}

\begin{corollary}[Visible stage-\texorpdfstring{$5$}{5} local conjecture network collapses
to one nontrivial singleton under principal normal form;
\ClaimStatusProvedHere]
\label{cor:winfty-stage5-visible-conjecture-network-collapse}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-effective-independent-frontier},
and
Conjecture~\ref{conj:winfty-stage5-principal-one-coefficient-normal-form}.
Then on the full visible
\texorpdfstring{$W^{(3)}$}{W3}/\texorpdfstring{$W^{(4)}$}{W4}/\texorpdfstring{$W^{(5)}$}{W5}
pairing locus:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the packet conjecture
  Conjecture~\ref{conj:winfty-stage5-higher-spin-identities}, the
  entry/transport conjectures
  Conjectures~\ref{conj:winfty-stage5-entry-identities}
  and~\ref{conj:winfty-stage5-transport-identities}, the target-$3$ and
  target-$4$ ladder conjectures
  Conjectures~\ref{conj:winfty-stage5-transport-target-3}
  and~\ref{conj:winfty-stage5-transport-target-4}, and the block
  conjectures
  Conjectures~\ref{conj:winfty-stage5-block-34}
  --\ref{conj:winfty-stage5-block-45} are each equivalent to the single
  identity of
  Conjecture~\ref{conj:winfty-stage5-one-coefficient-comparison};
\item the target-$5$ ladder conjecture
  Conjecture~\ref{conj:winfty-stage5-transport-target-5}, its two
  singleton refinements
  Conjectures~\ref{conj:winfty-stage5-transport-target5-35}
  and~\ref{conj:winfty-stage5-transport-target5-45}, and the self-block
  conjecture
  Conjecture~\ref{conj:winfty-stage5-block-55} become automatic.
\end{enumerate}
In particular, once the packaged principal one-coefficient normal form
is granted, the local stage-$5$ conjecture tree below
\(\mathcal{J}_5^{\mathrm{hs}}\) has exactly one nontrivial comparison
input, namely the target-$4$ singleton \((3,5;4;0,4)\).
\end{corollary}

\begin{proof}
Under the one-coefficient normal form on both sides, each block conjecture is either automatic (self-block, target-$5$ ladder: all channels vanish on both sides) or equivalent to the singleton identity \(\mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}=\mathsf{C}^{\mathrm{DS}}_{3,5;4;0,4}\) via the fixed rational multiples \(-\tfrac54\) (mixed-entry), \(1\) (representative), and \(-\tfrac34\) (target-$3$).  The entry, transport, and packet conjectures are conjunctions of these, hence each equivalent to the singleton identity.
\end{proof}

\begin{corollary}[Visible stage-\texorpdfstring{$5$}{5} local defect classes under principal
normal form; \ClaimStatusProvedHere]
\label{cor:winfty-stage5-visible-defect-classes}
Assume the hypotheses of
Corollary~\ref{cor:winfty-stage5-visible-conjecture-network-collapse},
and set
\[
D_5:=
\mathsf{C}^{\mathrm{res}}_{3,5;4;0,4}(5)
-
\mathsf{C}^{\mathrm{DS}}_{3,5;4;0,4}(5).
\]
Then the downstream local stage-$5$ conjectural surfaces on the full
visible
\texorpdfstring{$W^{(3)}$}{W3}/\texorpdfstring{$W^{(4)}$}{W4}/\texorpdfstring{$W^{(5)}$}{W5}
pairing locus split into the following exact defect classes:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the mixed-entry block
  Conjecture~\ref{conj:winfty-stage5-block-34} carries defect
  \[
  \mathsf{C}^{\mathrm{res}}_{3,4;5;0,2}(5)
  -
  \mathsf{C}^{\mathrm{DS}}_{3,4;5;0,2}(5)
  =
  -\frac{5}{4}\,D_5;
  \]
\item the representative target-$4$ class consists of the singleton
  comparison
  Conjecture~\ref{conj:winfty-stage5-one-coefficient-comparison}, the
  target-$4$ ladder
  Conjecture~\ref{conj:winfty-stage5-transport-target-4}, and the
  \texorpdfstring{$(3,5)$}{(3,5)} block
  Conjecture~\ref{conj:winfty-stage5-block-35}, with representative
  defect exactly \(D_5\);
\item the target-$3$ class consists of the target-$3$ ladder
  Conjecture~\ref{conj:winfty-stage5-transport-target-3} and the
  \texorpdfstring{$(4,5)$}{(4,5)} block
  Conjecture~\ref{conj:winfty-stage5-block-45}, with representative
  defect
  \[
  \mathsf{C}^{\mathrm{res}}_{4,5;3;0,6}(5)
  -
  \mathsf{C}^{\mathrm{DS}}_{4,5;3;0,6}(5)
  =
  -\frac{3}{4}\,D_5;
  \]
\item the target-$5$ ladder
  Conjecture~\ref{conj:winfty-stage5-transport-target-5}, its singleton
  refinements
  Conjectures~\ref{conj:winfty-stage5-transport-target5-35}
  and~\ref{conj:winfty-stage5-transport-target5-45},
  and the self-block
  Conjecture~\ref{conj:winfty-stage5-block-55}
  are automatic, so their defects vanish.
\end{enumerate}
Equivalently, every nonautomatic local stage-$5$ visible-pairing
surface lies in one of the three exact defect classes
\(-\tfrac54 D_5\), \(D_5\), or \(-\tfrac34 D_5\).
\end{corollary}

\begin{proof}
The fixed ratios from Corollary~\ref{cor:winfty-stage5-visible-conjecture-network-collapse} give defects \(-\tfrac54 D_5\), \(D_5\), and \(-\tfrac34 D_5\); automatic channels have zero defect.
\end{proof}

\begin{computation}[Full stage-\texorpdfstring{$4$}{4} reduction chain verification]
\label{comp:winfty-stage4-reduction-chain}
\index{MC4!W-infinity stage-4 reduction chain}
The complete reduction chain from the residual packet
$\mathcal{J}_4$ to the frontier of
Proposition~\ref{prop:winfty-mc4-frontier-package} has been
verified computationally
(\texttt{compute/lib/w4\_stage4\_coefficients.py}, $85$~tests):
\begin{itemize}
\item \emph{Primaryity}
  (Corollary~\ref{cor:winfty-ds-stage4-top-pole-packet}):
  $|\mathcal{J}_4| = 29 \to |\mathcal{J}_4^{\mathrm{top}}| = 7$,
  eliminating $22$ sub-leading entries; seven top-pole elements
  verified against the manuscript display;
\item \emph{Parity}
  (Corollary~\ref{cor:winfty-ds-stage4-parity-packet}):
  $|\mathcal{J}_4^{\mathrm{top}}| = 7
  \to |\mathcal{J}_4^{\mathrm{par}}| = 6$,
  removing exactly $(4,4,3,5)$ (odd-spin self-OPE);
\item \emph{OPE blocks}
  (Corollary~\ref{cor:winfty-ds-stage4-ope-blocks}):
  $6 = 1 + 3 + 2$ as $(3,3)$, $(3,4)$, $(4,4)$ blocks;
\item \emph{Mixed-self split}
  (Corollary~\ref{cor:winfty-ds-stage4-mixed-self-split}):
  three self-coupling scalars $+$ three mixed channels;
\item \emph{Virasoro elimination}
  (Corollary~\ref{cor:winfty-ds-stage4-five-plus-zero}):
  $\mathsf{C}^{\mathrm{DS}}_{4,4;2;0,6} = 2$ (universal $T$-coupling)
  and $\mathsf{C}^{\mathrm{DS}}_{3,4;2;0,5} = 0$ (mixed vanishing)
  split the stage-$4$ packet into $4$ higher-spin channels plus
  $2$ theorematic principal Virasoro-target values.
\end{itemize}
The full chain $29 \to 7 \to 6 = 4 + 2$ matches every intermediate
cardinality and every explicit element of the manuscript displays.
\end{computation}

\begin{proposition}[Explicit \texorpdfstring{$W_4$}{W4} OPE structure constants;
\ClaimStatusProvedElsewhere]
\label{prop:w4-ds-ope-explicit}
In the principal Drinfeld--Sokolov reduction
$W_4 = W(\mathfrak{sl}_4, f_{\mathrm{prin}})$ with generators
$T$ (spin~$2$), $W^{(3)}$ (spin~$3$), $W^{(4)}$ (spin~$4$)
normalized so that
$\langle W^{(s)}(z)\,W^{(s)}(0)\rangle = (c/s)\,z^{-2s}$,
the four higher-spin stage-$4$ principal targets of
Corollary~\textup{\ref{cor:winfty-ds-stage4-five-plus-zero}} are
given by the following rational functions of the central charge~$c$:
\begin{align}
c_{334}^{\,2}
&= \frac{42\,c^2(5c+22)}{(c+24)(7c+68)(3c+46)},
\label{eq:c334-explicit}
\\[4pt]
c_{444}^{\,2}
&= \frac{112\,c^2(2c-1)(3c+46)}{(c+24)(7c+68)(10c+197)(5c+3)},
\label{eq:c444-explicit}
\\[4pt]
\mathsf{C}_{3,4;3;0,4}^{\,2}
&= \tfrac{9}{16}\,c_{334}^{\,2},
\label{eq:c343-explicit}
\\[4pt]
\mathsf{C}_{3,4;4;0,3}^{\,2}
&= \tfrac{5}{7}\,c_{334}^{\,2}.
\label{eq:c344-explicit}
\end{align}
The two theorematic Virasoro-target identities in
Corollary~\textup{\ref{cor:winfty-ds-stage4-five-plus-zero}} are
confirmed:
\begin{equation}
\mathsf{C}^{\mathrm{DS}}_{4,4;2;0,6} = 2,
\qquad
\mathsf{C}^{\mathrm{DS}}_{3,4;2;0,5} = 0.
\label{eq:w4-virasoro-target-identities-verified}
\end{equation}
\end{proposition}

\begin{proof}
The structure constants follow from the vertex-algebra Jacobi
identity (Borcherds identity) applied to the three-generator $W_4$
algebra.  Formula~\eqref{eq:c334-explicit} is the bootstrap result
of Hornfeck~\cite{Hornfeck93}; formula~\eqref{eq:c444-explicit}
then follows from the $(W^{(4)}, W^{(4)}, W^{(4)})$ Jacobi identity.
The inter-coefficient relations~\eqref{eq:c343-explicit}
and~\eqref{eq:c344-explicit} are metric-adjoint and Borcherds-identity
consequences of~\eqref{eq:c334-explicit}, respectively; see
Bouwknegt--Schoutens~\cite{Bouwknegt-Schoutens}
and Blumenhagen \textit{et al.}~\cite{BEHFH96}.
The universal $T$-coupling
$\mathsf{C}_{4,4;2;0,6}=2$ follows from
Proposition~\ref{prop:winfty-ds-self-t-coefficient}, and the mixed
Virasoro vanishing
$\mathsf{C}_{3,4;2;0,5}=0$ from
Proposition~\ref{prop:winfty-ds-mixed-virasoro-ds-zero}.
\end{proof}

\begin{corollary}[Principal stage-\texorpdfstring{$4$}{4} higher-spin packet from two
primitive square classes; \ClaimStatusProvedHere]
\label{cor:w4-ds-stage4-square-class-reduction}
In the setting of
Proposition~\ref{prop:w4-ds-ope-explicit}, the higher-spin part of the
principal stage-$4$ target packet is determined at signless
square-class level by the pair
\[
c_{334}^{\,2},
\qquad
c_{444}^{\,2}.
\]
More precisely, the two mixed higher-spin channels are forced by
$c_{334}^{\,2}$:
\[
\mathsf{C}_{3,4;3;0,4}^{\,2}
= \tfrac{9}{16}\,c_{334}^{\,2},
\qquad
\mathsf{C}_{3,4;4;0,3}^{\,2}
= \tfrac{5}{7}\,c_{334}^{\,2}.
\]
Consequently, after removing the theorematic Virasoro-target values
\[
\mathsf{C}^{\mathrm{DS}}_{4,4;2;0,6}=2,
\qquad
\mathsf{C}^{\mathrm{DS}}_{3,4;2;0,5}=0,
\]
the principal stage-$4$ DS packet does not require four primitive
higher-spin targets: it consists of the two primitive square classes
$c_{334}^{\,2},c_{444}^{\,2}$ together with two mixed square-class
descendants forced by~$c_{334}^{\,2}$.
\end{corollary}

\begin{proof}
The explicit formulas
\eqref{eq:c343-explicit} and~\eqref{eq:c344-explicit} express the two
mixed higher-spin squares directly in terms of~$c_{334}^{\,2}$, while
\eqref{eq:w4-virasoro-target-identities-verified} records the two
theorematic Virasoro-target values.  Hence the displayed pair
$c_{334}^{\,2},c_{444}^{\,2}$ is the entire primitive higher-spin
square-class input on the principal side.
\end{proof}

\begin{remark}[Exact stage-4 identity packet]
\label{rem:winfty-stage4-exact-identity-packet}
Proposition~\ref{prop:winfty-mc4-frontier-package} and
Proposition~\ref{prop:w4-ds-ope-explicit} together show that the first
genuinely higher-spin MC4 packet is no longer extraction of principal
Drinfeld--Sokolov data.  That side is already explicit.  The live
stage-$4$ task is the six bar-side identities
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(4)
=
\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(4)
\]
on the packet
\[
\Bigl\{
\begin{gathered}
(3,3;4;0,2),\,
(4,4;4;0,4),\\
(3,4;3;0,4),\,
(3,4;4;0,3),\,
(4,4;2;0,6),\\
(3,4;2;0,5)
\end{gathered}
\Bigr\}.
\]
For the first four channels, the DS targets are fixed by the explicit
formulas \eqref{eq:c334-explicit}--\eqref{eq:c344-explicit}, up to the
chosen strong-generator signs.  The last two channels are fixed exactly
by \eqref{eq:w4-virasoro-target-identities-verified}.  Thus the first open higher-spin
packet is an exact six-entry identity problem on~$\mathcal{I}_4$, not a
further principal-side extraction problem.
\end{remark}

\begin{computation}[Full \texorpdfstring{$W_4$}{W4} OPE coefficient extraction]
\label{comp:w4-ds-ope-extraction}
\index{MC4!W4 OPE coefficient extraction}
The explicit structure constants of
Proposition~\ref{prop:w4-ds-ope-explicit} have been verified
computationally
(\texttt{compute/lib/w4\_ds\_ope\_extraction.py}, $121$~tests):
\begin{itemize}
\item all four squared structure constants evaluated at levels
  $k = 0, 1, 2, -2, -3$ (avoiding poles);
\item inter-coefficient ratios
  $\mathsf{C}_{3,4;3;0,4}^2/c_{334}^2 = 9/16$ and
  $\mathsf{C}_{3,4;4;0,3}^2/c_{334}^2 = 5/7$ verified symbolically;
\item Feigin--Frenkel duality $k \leftrightarrow -k-2h^\vee$
  checked: $c(k) + c(-k-8) = 246$;
\item unitarity non-negativity ($c_{334}^2 \geq 0$, $c_{444}^2 \geq 0$)
  confirmed at all $\mathcal{W}(N, N{+}1)$ minimal models
  for $4 \leq N \leq 19$;
\item both theorematic principal Virasoro-target values
  $\mathsf{C}^{\mathrm{DS}}_{4,4;2;0,6} = 2$ and
  $\mathsf{C}^{\mathrm{DS}}_{3,4;2;0,5} = 0$ confirmed.
\end{itemize}
\end{computation}

\subsection{Maurer--Cartan elements and deformation theory}
\label{sec:maurer-cartan-curved}

\begin{definition}[Maurer--Cartan element in curved context]
\label{def:mc-element-curved}
For a curved $A_\infty$ algebra $(A, \{\mu_n\})$, a \emph{Maurer--Cartan element} is $\alpha 
\in A^1$ satisfying:
\begin{equation}
\sum_{n \geq 0} \mu_n(\alpha^{\otimes n}) = 0
\end{equation}
\end{definition}

\begin{theorem}[Twisting by MC elements {\cite{LV12}}; \ClaimStatusProvedElsewhere]
\label{thm:twisting-mc}
Given an MC element $\alpha$, we can twist the curved $A_\infty$ structure:
\begin{equation}
\mu_n^\alpha(a_1, \ldots, a_n) = \sum_{k \geq 0} \mu_{n+k}(\alpha^{\otimes k}, 
a_1, \ldots, a_n)
\end{equation}

The twisted structure $(A, \{\mu_n^\alpha\})$ is again a curved $A_\infty$ algebra, with new 
curvature:
\begin{equation}
\mu_0^\alpha = \mu_0 + \mu_1(\alpha) + \frac{1}{2}\mu_2(\alpha, \alpha) + \cdots
\end{equation}

If $\alpha$ is an MC element, then $\mu_0^\alpha = 0$, so the twisted structure is 
\emph{uncurved}.
\end{theorem}

\begin{remark}[Physical interpretation]
MC elements correspond to \emph{vacua} (different ground states of the theory), \emph{deformations} (continuous families parametrized by the MC equation), and \emph{obstructions} (failure of the MC equation means curvature persists).
\end{remark}

\subsection{Summary and comparison table}
\label{sec:curved-summary}

\begin{table}[ht]
\centering
\caption{Quadratic, curved, and filtered structures}
\begin{tabular}{|l|c|c|c|}
\hline
\textbf{Property} & \emph{Quadratic} & \emph{Curved} & \emph{Filtered}\\
\hline
Curvature μ₀ & 0 & ∈ Z(A) & Multiple\\
Completion needed? & No & Sometimes & Usually\\
Koszul dual exists? & Yes & Yes (with completion) & Sometimes\\
Example & Heisenberg & Virasoro & W₃\\
\hline
\end{tabular}
\end{table}

The hierarchy is therefore:
\begin{equation}
\text{Quadratic} \subset \text{Curved} \subset \text{Filtered}
\end{equation}

Each level requires more sophisticated technology (completion, filtered cooperads), but 
also captures more examples from physics and representation theory.

\section{\texorpdfstring{Curved $A_\infty$ structures: strict vs.\ homotopy nilpotence}{Curved A-infinity structures: strict vs homotopy nilpotence}}
\label{sec:strict-vs-homotopy}

For chiral algebras $\mathcal{A}$ with quantum corrections at genus $g$,
the curvature $\mu_0$ controls two distinct squares:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Algebraic:}\; $m_1^2(a) = [\mu_0, a]$.
  When $\mu_0 \in Z(\mathcal{A})$, this vanishes for all~$a$, so $m_1$ is a strict differential on~$\mathcal{A}$.  All standard chiral algebras (Heisenberg, Kac--Moody, Virasoro, $\mathcal{W}$-algebras) satisfy this because their central extensions are central.
\item \emph{Geometric:}\; $\dfib^{\,2} = \kappa(\mathcal{A})\cdot\omega_g \neq 0$ whenever $\kappa(\mathcal{A}) \neq 0$
  (Convention~\ref{conv:higher-genus-differentials}).
  Even when $\mu_0$ is central, the fiberwise bar differential over~$\overline{\mathcal{M}}_g$ is \emph{not} nilpotent---its failure is controlled by the scalar invariant~$\kappa(\mathcal{A})$.
\end{enumerate}
The total corrected differential $\Dg{g}$ absorbs the geometric curvature and satisfies $\Dg{g}^{\,2} = 0$ unconditionally (Theorem~\ref{thm:quantum-diff-squares-zero}).

\subsection{Mathematical foundations: three regimes}
\label{subsec:three-regimes}

The three regimes below correspond to the first three levels of the
regime hierarchy (Convention~\ref{conv:regime-tags}): quadratic
(Regime~I), curved-central (Regime~II), and filtered-complete
(Regime~III).  The fourth level (programmatic) lies beyond the
scope of the present chapter.

\subsubsection{\texorpdfstring{Regime I: strict differential ($d^2 = 0$ strict)}{Regime I: strict differential (d2 = 0 strict)}}

\begin{definition}[Strict dg structure]\label{def:strict-dg}
A \emph{strict differential graded structure} consists of:
\begin{itemize}
\item A graded vector space $V = \bigoplus_{n \in \mathbb{Z}} V^n$
\item A linear map $d: V^n \to V^{n+1}$ of degree $+1$
\item Satisfying $d \circ d = 0$ \emph{exactly}, not just up to homotopy
\end{itemize}
\end{definition}

\begin{example}[De Rham complex]
The de Rham complex $(\Omega^*(X), d_{dR})$ on a smooth manifold $X$:
\[\cdots \to \Omega^{n-1}(X) \xrightarrow{d_{dR}} \Omega^n(X) \xrightarrow{d_{dR}} 
\Omega^{n+1}(X) \to \cdots\]

Here $d_{dR}^2 = 0$ \emph{strict} because:
\[d_{dR}^2(f dx^{i_1} \wedge \cdots \wedge dx^{i_k}) 
= \sum_{j < k} \frac{\partial^2 f}{\partial x^j \partial x^k} dx^j \wedge dx^k \wedge dx^{i_1} 
\wedge \cdots = 0\]
by commutativity of partial derivatives.

\end{example}

\subsubsection{\texorpdfstring{Regime II: curved differential ($m_1^2 = [\mu_0, -]$, central curvature)}{Regime II: curved differential (m1 squared = commutator with mu0, central curvature)}}

% Duplicate curved A-infinity definition commented out.
% Canonical version: Definition~\ref{def:curved-ainfty} (line ~4866).
% Alias label preserved for any stale external references.
\label{def:curved-ainfty-complete}
\iffalse
%%% BEGIN COMMENTED-OUT BLOCK 4: duplicate curved A-infinity definition
%%% Canonical version lives at def:curved-ainfty (~line 4866).
\begin{definition}[Curved \texorpdfstring{$A_\infty$}{A_infinity} algebra]\label{def:curved-ainfty-complete-DISABLED}
A \emph{curved $A_\infty$ algebra} $(\mathcal{A}, \{m_k\}_{k \geq 0}, \mu_0)$ consists of:
\begin{enumerate}
\item A $\mathbb{Z}$-graded vector space $\mathcal{A} = \bigoplus_{n} \mathcal{A}^n$
\item Operations $m_k: \mathcal{A}^{\otimes k} \to \mathcal{A}[2-k]$ for each $k \geq 0$
\item A \emph{curvature element} $\mu_0 \in \mathcal{A}^2$
\end{enumerate}
satisfying the \emph{curved $A_\infty$ relations}:
\begin{equation}\label{eq:curved-ainfty-relations-DISABLED}
\sum_{\substack{r+s+t=n \\ r,t \geq 0, \, s \geq 0}} (-1)^{rs+t} m_{r+1+t}
(\text{id}^{\otimes r} \otimes m_s \otimes \text{id}^{\otimes t}) = 0
\end{equation}

The special cases of low degree are:
\begin{itemize}
\item $n = 0$: $m_1(m_0) = 0$ \quad (curvature is a $m_1$-cycle)
\item $n = 1$: $m_1^2(a) = m_2(m_0 \otimes \text{id})(a) - m_2(\text{id} \otimes m_0)(a)$
\quad (failure of $d^2 = 0$)
\item $n = 2$: Higher coherences involving $\mu_0$
\end{itemize}
\end{definition}
%%% END COMMENTED-OUT BLOCK 4
\fi

\begin{theorem}[Centrality implies strict nilpotence; \ClaimStatusProvedHere]\label{thm:central-implies-strict}
For the Heisenberg algebra on an elliptic curve (\S\ref{sec:frame-genus1}), the curvature $d^2 = k \cdot \omega_1$ was scalar, hence central.  Centrality of the curvature is the general mechanism ensuring $d^2 = 0$ strictly in the curved setting.

Let $(\mathcal{A}, m_1, \mu_0)$ be a curved chiral algebra with curvature satisfying:
\begin{equation}
\mu_0 \in Z(\mathcal{A}) := \{a \in \mathcal{A} \mid m_2(a \otimes b) = (-1)^{|a||b|}m_2(b \otimes a)
\text{ for all } b\}
\end{equation}
then the bar differential satisfies:
\begin{equation}
d_{\text{bar}}^2 = 0 \quad \emph{strictly}
\end{equation}
\end{theorem}

\begin{proof}

\emph{Step 1: Bar Differential Formula}

Recall from \S\ref{def:bar-differential-complete} that the bar differential on 
$\bar{B}^n(\mathcal{A})$ has three components:
\begin{equation}
d_{\text{bar}} = d_{\text{internal}} + d_{\text{residue}} + d_{\text{correction}}
\end{equation}
where:
\begin{align}
d_{\text{internal}}(a_0 \otimes \cdots \otimes a_n) 
&= \sum_{i=0}^n (-1)^{|a_0| + \cdots + |a_{i-1}|} (a_0 \otimes \cdots \otimes m_1(a_i) 
\otimes \cdots \otimes a_n) \\
d_{\text{residue}}(a_0 \otimes \cdots \otimes a_n) 
&= \sum_{i=0}^{n-1} (-1)^{\epsilon_i} \text{Res}_{D_i}(a_0 \otimes \cdots \otimes a_i \cdot a_{i+1} 
\otimes \cdots \otimes a_n) \\
d_{\text{correction}}(a_0 \otimes \cdots \otimes a_n) 
&= \mu_0 \otimes (a_0 \otimes \cdots \otimes a_n) \otimes \omega_g
\end{align}

\emph{Step 2: Computing $d^2$ - Nine Terms}

We need to compute:
\begin{equation}
d_{\text{bar}}^2 = (d_{\text{internal}} + d_{\text{residue}} + d_{\text{correction}})^2
\end{equation}

This expands to \emph{nine terms}:
\begin{align}
d_{\text{bar}}^2 &= d_{\text{internal}}^2 
+ d_{\text{internal}} d_{\text{residue}} + d_{\text{residue}} d_{\text{internal}} \\
&\quad + d_{\text{residue}}^2 \\
&\quad + d_{\text{internal}} d_{\text{correction}} + d_{\text{correction}} d_{\text{internal}} \\
&\quad + d_{\text{residue}} d_{\text{correction}} + d_{\text{correction}} d_{\text{residue}} \\
&\quad + d_{\text{correction}}^2
\end{align}

\emph{Term 1: $d_{\text{internal}}^2$}

For a \emph{curved} $A_\infty$ algebra, $m_1^2 \neq 0$ in general. The $n=1$ curved $A_\infty$ relation (Eq.~\ref{eq:curved-ainfty-relations}) gives:
\begin{equation}\label{eq:curved-m1-squared}
m_1^2(a) = m_2(\mu_0 \otimes a) - m_2(a \otimes \mu_0)
\end{equation}
Therefore $d_{\text{internal}}^2 \neq 0$ when the curvature $\mu_0$ is nonzero. This contribution is cancelled by terms 5--6 below (the cross-terms with $d_{\text{correction}}$); see the combined analysis there.

\emph{Term 2-3: $d_{\text{internal}} d_{\text{residue}} + d_{\text{residue}} d_{\text{internal}} = 0$}

These cancel by the \emph{Leibniz rule}:
\begin{equation}
m_1(a \cdot b) = m_1(a) \cdot b + (-1)^{|a|} a \cdot m_1(b)
\end{equation}

Explicitly, using residue calculus:
\begin{align}
&d_{\text{internal}}(\text{Res}_{D_i}(a_0 \otimes \cdots)) 
= \text{Res}_{D_i}(m_1(a_i \cdot a_{i+1})) \\
&= \text{Res}_{D_i}(m_1(a_i) \cdot a_{i+1}) + \text{Res}_{D_i}(a_i \cdot m_1(a_{i+1})) 
\quad \text{(Leibniz)} \\
&= d_{\text{residue}}(d_{\text{internal}}(a_0 \otimes \cdots))
\end{align}

Therefore the cross terms cancel: 
\[d_{\text{internal}} d_{\text{residue}} = - d_{\text{residue}} d_{\text{internal}}\]

\emph{Term 4: $d_{\text{residue}}^2 = 0$ (Arnold Relations)}

By Theorem~\ref{thm:arnold-three}:
\begin{equation}
\eta_{ij} \wedge \eta_{jk} + \eta_{jk} \wedge \eta_{ki} + \eta_{ki} \wedge \eta_{ij} = 0
\end{equation}
in $H^2(\text{Conf}_n(X))$.

Geometrically, this means:
\begin{equation}
[\text{Res}_{D_{ij}}, \text{Res}_{D_{jk}}] + [\text{Res}_{D_{jk}}, \text{Res}_{D_{ki}}] 
+ [\text{Res}_{D_{ki}}, \text{Res}_{D_{ij}}] = 0
\end{equation}

Therefore:
\[d_{\text{residue}}^2 = \sum_{i,j} \text{Res}_{D_i} \text{Res}_{D_j} 
= 0 \quad \text{(by Arnold)}\]

\emph{Terms 1+5+6 combined: $d_{\text{internal}}^2 + d_{\text{internal}} d_{\text{correction}} + d_{\text{correction}} d_{\text{internal}} = 0$}

These three terms must be analyzed together. We have:
\begin{align}
d_{\text{internal}}(d_{\text{correction}}(a_0 \otimes \cdots))
&= d_{\text{internal}}(\mu_0 \otimes a_0 \otimes \cdots) \\
&= m_1(\mu_0) \otimes (a_0 \otimes \cdots) + \sum_i \mu_0 \otimes \cdots \otimes m_1(a_i) \otimes \cdots
\end{align}
and similarly for $d_{\text{correction}} d_{\text{internal}}$. The cross-terms produce:
\begin{equation}
\begin{aligned}
&(d_{\text{internal}} d_{\text{correction}} + d_{\text{correction}} d_{\text{internal}})
(a_0 \otimes \cdots) \\
&\quad = m_1(\mu_0) \otimes (a_0 \otimes \cdots)
 + \sum_i \pm\bigl(
a_0 \otimes \cdots \otimes m_2(\mu_0, a_i)
 + m_2(a_i, \mu_0) \otimes \cdots
\bigr).
\end{aligned}
\end{equation}
By the curved $A_\infty$ relation~\eqref{eq:curved-m1-squared}: $m_1^2(a_i) = m_2(\mu_0, a_i) - m_2(a_i, \mu_0)$. Since $\mu_0$ is a \emph{cycle} ($m_1(\mu_0) = 0$), the combined contribution is:
\[d_{\text{internal}}^2 + d_{\text{internal}} d_{\text{correction}} + d_{\text{correction}} d_{\text{internal}} = 0\]

\emph{Terms 7-8: $d_{\text{residue}} d_{\text{correction}} + d_{\text{correction}} 
d_{\text{residue}}$}

Centrality of $\mu_0$ is essential here.

We have:
\begin{align}
d_{\text{residue}}(d_{\text{correction}}(a_0 \otimes \cdots)) 
&= d_{\text{residue}}(\mu_0 \otimes a_0 \otimes \cdots) \\
&= \sum_i \text{Res}_{D_i}((\mu_0 \otimes a_0 \otimes \cdots \otimes a_i \cdot a_{i+1} 
\otimes \cdots))
\end{align}

For this to equal $d_{\text{correction}}(d_{\text{residue}}(\cdots))$, we need:
\begin{equation}
\text{Res}_{D_i}(\mu_0 \otimes \cdots) = \mu_0 \otimes \text{Res}_{D_i}(\cdots)
\end{equation}

This holds if and only if $\mu_0 \in Z(\mathcal{A})$.

\emph{Proof of centrality.}
The residue operation involves computing:
\[\text{Res}_{z_i = z_{i+1}}(m_2(a_i \otimes a_{i+1}))\]

If $\mu_0$ is central, it commutes with all $a_i$:
\[m_2(\mu_0 \otimes a_i) = m_2(a_i \otimes \mu_0)\]

Therefore:
\begin{align}
\text{Res}_{D_i}(\mu_0 \otimes a_0 \otimes \cdots \otimes m_2(a_i \otimes a_{i+1}) \otimes \cdots) 
&= \text{Res}_{D_i}(m_2(\mu_0 \otimes a_0) \otimes \cdots) \\
&= \text{Res}_{D_i}(m_2(a_0 \otimes \mu_0) \otimes \cdots) \quad \text{(by centrality)} \\
&= \mu_0 \otimes \text{Res}_{D_i}(a_0 \otimes \cdots)
\end{align}

\emph{Term 9: $d_{\text{correction}}^2$}

Finally:
\begin{align}
d_{\text{correction}}^2(a_0 \otimes \cdots) 
&= d_{\text{correction}}(\mu_0 \otimes a_0 \otimes \cdots) \\
&= \mu_0 \otimes \mu_0 \otimes (a_0 \otimes \cdots) \otimes \omega_g^2
\end{align}

This term involves the commutator $[\mu_0, -]$ acting on bar elements.  When $\mu_0 \in Z(\mathcal{A})$, the commutator $[\mu_0, -]_{\mu_2} = 0$ vanishes identically, so this term is zero regardless of $\omega_g^2$.

(When $\mu_0 \notin Z(\mathcal{A})$, the term $d_{\mathrm{correction}}^2$ produces the genus-$g$ obstruction class $\mathrm{Obs}_g(\mathcal{A}) = [\mu_0, -] \otimes \int_{\mathcal{M}_g} \omega_g \cup \omega_g \neq 0$; see Remark~\ref{rem:non-central-curvature}.)

Combining all nine terms:
\begin{equation}
d_{\text{bar}}^2 = 0 + 0 + 0 + 0 + 0 + 0 + 0 = 0 \quad \text{strictly}
\end{equation}
provided $\mu_0 \in Z(\mathcal{A})$.

\end{proof}

\begin{remark}[What if \texorpdfstring{$\mu_0 \notin Z(\mathcal{A})$}{mu0 not in Z(A)}?]\label{rem:non-central-curvature}
If the curvature is \emph{not central}, then:
\begin{equation}
d_{\text{bar}}^2 \neq 0
\end{equation}
and we only have $d_{\text{bar}}^2 = 0$ \emph{up to homotopy}.

This leads to:
\begin{itemize}
\item \emph{Homotopy coherent structures} (Lurie, Higher Topos Theory)
\item \emph{Spectral sequences that may not degenerate}
\item \emph{Obstruction theories with non-closed obstructions}
\item \emph{Need for $A_\infty$ or $L_\infty$ structures at all levels}
\end{itemize}

However, \emph{all our examples} (Heisenberg, Kac--Moody, Virasoro, W-algebras) have
\emph{central curvature}, so we obtain strict nilpotence.  See
Remark~\ref{rem:voa-central-curvature} for the precise mechanism.
\end{remark}

\begin{remark}[Central curvature in vertex operator algebras]\label{rem:voa-central-curvature}
For vertex operator algebras, the vacuum axiom guarantees that the vacuum vector
$\mathbf{1}\in V$ is central: $Y(\mathbf{1},z) = \mathrm{id}_V$.  In the curved
$A_\infty$ framework, the curvature element $\mu_0$ arising from the genus-$g$
quantum correction is proportional to $\mathbf{1}$ (it equals the central charge or
level times $\mathbf{1}$; see Examples~\ref{ex:heisenberg-strict}--\ref{ex:w3-strict}).
Since $\mathbf{1}$ acts by the identity on every module, $\mu_0$ lies in $Z(\mathcal{A})$,
and Theorem~\ref{thm:central-implies-strict} yields $d_{\mathrm{bar}}^2=0$ strict.

For more general chiral algebras without a vacuum axiom --- for instance, chiral
algebras on higher-dimensional varieties, or non-unital factorization algebras ---
the curvature need not be central, and $d^2=0$ may hold only up to homotopy.
Similarly, chiral algebras arising from field theories with non-central anomalies
(such as gravitational anomalies that act non-trivially on the operator algebra)
fall outside the scope of Theorem~\ref{thm:central-implies-strict}.
\end{remark}

\subsubsection{\texorpdfstring{Regime III: general homotopy coherent ($d^2 \sim 0$ via homotopy)}{Regime III: general homotopy coherent (d2 0 via homotopy)}}

\begin{definition}[Homotopy coherent differential]\label{def:homotopy-coherent}
A \emph{homotopy coherent differential} on a graded space $V$ consists of:
\begin{itemize}
\item $d_1: V \to V[1]$ (the ``differential'')
\item $h: V \to V[-1]$ (a homotopy)
\item Satisfying: $d_1^2 = [d_1, h]$ (not zero, but homotopic to zero)
\item Plus higher coherence homotopies $h_2, h_3, \ldots$ ad infinitum
\end{itemize}
\end{definition}

This is the setting of Lurie's $(\infty, 1)$-categories~\cite{HTT}, derived algebraic geometry (To\"en--Vezzosi, Lurie), and non-curved $A_\infty$ or $L_\infty$ structures.

We do not need this level of generality for the chiral algebras studied in this monograph, since their curvature elements are central (see Remark~\ref{rem:voa-central-curvature} below).

\subsection{Application to chiral algebras: four examples}

\subsubsection{\texorpdfstring{Example 1: Heisenberg algebra (level $k$)}{Example 1: Heisenberg algebra (level k)}}

\begin{example}[Heisenberg: strict nilpotence]\label{ex:heisenberg-strict}
The Heisenberg algebra $\mathcal{H}_k$ has OPE $J(z)J(w) = k/(z-w)^2 + \text{reg.}$, curvature $\mu_0 = k \cdot \mathbf{1}$, and $\mu_0 \in Z(\mathcal{H}_k)$ since $\mathbf{1}$ is central.

\emph{Consequence.} The bar differential satisfies:
\[d_{\text{bar}}^2 = 0 \quad \text{strictly}\]

\emph{Genus 1 correction.}
At genus 1, the differential includes the term:
\[d_1 = d_0 + k \cdot \int_{\mathcal{M}_1} \omega_1\]
where $\omega_1 \in H^*(\mathcal{M}_1, \mathcal{Z}(\mathcal{A}))$ is the genus-1 quantum correction class.  (Here $\mathcal{M}_1 \cong \mathbb{H}/\mathrm{SL}_2(\mathbb{Z})$ is one-dimensional.)

This modifies $d_0$ but still $d_1^2 = 0$ strictly because $k$ is central.

\emph{Explicit verification at genus $1$.}
\begin{align}
d_1^2(J \otimes J) &= d_1(d_1(J \otimes J)) \\
&= d_1\left(\text{Res}_{z=w}(J(z)J(w)) + k \cdot \omega_1 \otimes J\right) \\
&= d_1\left(\frac{k}{(z-w)^2} dz \, dw + k \cdot \omega_1 \otimes J\right) \\
&= \text{Res}_{z=w}\left(\frac{k}{(z-w)^2}\right) + k \cdot \omega_1 \otimes \text{Res}(J) 
+ k \cdot \omega_1^2 \\
&= 0 + 0 + 0 = 0 \quad \text{(strictly)}
\end{align}

The $\omega_1^2$ term vanishes because $\dim \mathcal{M}_1 = 1$, so $H^2(\mathcal{M}_1) = 0$.
\end{example}

\subsubsection{\texorpdfstring{Example 2: affine Kac--Moody (level $k$)}{Example 2: affine Kac--Moody (level k)}}

\begin{example}[Kac--Moody: strict nilpotence]\label{ex:kac-moody-strict}
For $\widehat{\mathfrak{g}}_k$ with OPE $J^a(z)J^b(w) = k\kappa^{ab}/(z-w)^2 + f^{abc}J^c(w)/(z-w) + \text{reg.}$, the curvature is $\mu_0 = k \cdot K$ where $K$ generates the one-dimensional center.

\emph{Consequence.} Again $d_{\text{bar}}^2 = 0$ strict.

\emph{Higher genus.}
At genus $g$, the correction involves:
\[\mu_0^{(g)} = k \cdot \lambda_g \in H^2(\mathcal{M}_g, Z(\widehat{\mathfrak{g}}_k))\]
where $\lambda_g$ is a Hodge class.

Since $\mu_0^{(g)}$ is central, all higher genus bar differentials square to zero strictly.
\end{example}

\subsubsection{\texorpdfstring{Example 3: Virasoro algebra (central charge $c$)}{Example 3: Virasoro algebra (central charge c)}}

\begin{example}[Virasoro: curved but strict]\label{ex:virasoro-strict}
The Virasoro algebra $\text{Vir}_c$ has stress tensor $T$ with OPE
\[T(z)T(w) = \frac{c/2}{(z-w)^4} + \frac{2T(w)}{(z-w)^2} + \frac{\partial T(w)}{z-w} + \cdots\]
and curvature $\mu_0 = c \cdot \mathbf{1}$ from the central charge, which is a central element.

\emph{Subtlety.} The Virasoro algebra has \emph{higher order corrections}:
\[m_3(T \otimes T \otimes T) \neq 0\]
due to the cubic Schwarzian derivative term.

However, the \emph{curvature} $\mu_0 = c \cdot \mathbf{1}$ is still central, so:
\[d_{\text{bar}}^2 = 0 \quad \text{strictly}\]

\emph{Physical interpretation.}
The central charge $c$ measures the \emph{conformal anomaly}. It is a quantum correction
that breaks classical conformal invariance, but it does so in a central way ---
it does not break associativity of the OPE algebra.
\end{example}

\subsubsection{\texorpdfstring{Example 4: $W_3$ algebra}{Example 4: W-3 algebra}}

\begin{example}[\texorpdfstring{$W_3$}{W3}: filtered, still strict]\label{ex:w3-strict}
The $W_3$ algebra has generators $L$ (dimension~2, generating Virasoro with central charge~$c$) and $W$ (dimension~3, a primary field), with non-linear OPE: $W(z)W(w)$ involves composite operators.

\emph{Curvature.}
\[\mu_0 = c \cdot \mathbf{1} + \beta \cdot (\text{higher order central terms})\]

Both $c$ and the higher corrections are central, so:
\[d_{\text{bar}}^2 = 0 \quad \text{strictly}\]

Even though $W_3$ is \emph{not quadratic} and requires \emph{filtered}
structure, the curvature is still central, giving strict nilpotence.

\emph{Completion needed.}
For $W_3$, we need \emph{nilpotent completion} (see Appendix~\ref{app:nilpotent-completion}):
\[\widehat{\bar{B}}(W_3) = \varprojlim_n \bar{B}(W_3)/I^n\]
where $I$ is the augmentation ideal.

But once completed, $d_{\text{bar}}^2 = 0$ strictly on the completed complex.
\end{example}

% Duplicate MC subsection commented out.
% Canonical MC definition: def:mc-element-curved (~line 11255).
% Canonical twisting theorem: thm:twisting-mc (~line 11263).
% Alias labels preserved for external references (koszul_reference.tex).
\label{def:maurer-cartan}%
\label{eq:mc-equation}%
\label{thm:mc-deformations}%
\label{thm:mc-periods}%
\iffalse
%%% BEGIN COMMENTED-OUT BLOCK 1: duplicate MC definition and deformation theory
%%% Canonical MC definition lives at def:mc-element-curved (~line 11255).
%%% Canonical twisting theorem lives at thm:twisting-mc (~line 11263).
\subsection{Maurer--Cartan elements and deformations}

\subsubsection{Maurer--Cartan equation}

\begin{definition}[Maurer--Cartan element]\label{def:maurer-cartan-DISABLED}
\index{Maurer--Cartan!chiral}
An element $\alpha \in \mathcal{A}^1$ is a \emph{Maurer--Cartan (MC) element} if it satisfies:
\begin{equation}\label{eq:mc-equation-DISABLED}
m_1(\alpha) + \frac{1}{2} m_2(\alpha \otimes \alpha) + \frac{1}{3!} m_3(\alpha \otimes \alpha
\otimes \alpha) + \cdots + \mu_0 = 0
\end{equation}
\end{definition}

\begin{theorem}[MC elements as quantum deformations; \ClaimStatusProvedHere]\label{thm:mc-deformations-DISABLED}
Maurer--Cartan elements in $\bar{B}^1(\mathcal{A})$ correspond to:
\begin{enumerate}
\item \emph{Physically:} Quantum deformations of the classical algebra
\item \emph{Geometrically:} Flat connections on the associated bundle
\item \emph{Algebraically:} Twisted differentials $d_\alpha = d + [\alpha, -]$
\end{enumerate}

If $\alpha$ is an MC element, then:
\begin{equation}
d_\alpha^2 = 0 \quad \text{strictly} \quad \Longleftrightarrow \quad \mu_0^\alpha := \mu_0
+ m_1(\alpha) + \cdots = 0
\end{equation}
is central.
\end{theorem}

\begin{proof}
Define the twisted differential:
\[d_\alpha := d + m_1(\alpha \otimes -) + m_2(\alpha \otimes \alpha \otimes -) + \cdots\]

Then:
\begin{align}
d_\alpha^2 &= (d + m_1(\alpha \otimes -) + \cdots)^2 \\
&= d^2 + d(m_1(\alpha \otimes -)) + m_1(\alpha \otimes -)^2 + \cdots \\
&= [m_1(\alpha) + \frac{1}{2}m_2(\alpha \otimes \alpha) + \cdots + \mu_0, -]
\end{align}

By the $A_\infty$ relations, this equals:
\[d_\alpha^2 = [\mu_0^\alpha, -]\]
where $\mu_0^\alpha$ is the \emph{twisted curvature}.

Therefore $d_\alpha^2 = 0$ strict if and only if $\mu_0^\alpha$ is central.
\end{proof}

\subsubsection{Geometric realization of MC elements}

\begin{theorem}[MC elements via period integrals; \ClaimStatusProvedHere]\label{thm:mc-periods-DISABLED}
For a chiral algebra $\mathcal{A}$ on a curve $X$ of genus $g$, Maurer--Cartan elements arise
from period integrals:
\begin{equation}
\alpha_g = \int_{\gamma \in H_1(X, \mathbb{Z})} \omega_{\mathcal{A}} \in \bar{B}^1(\mathcal{A})
\end{equation}
where $\omega_{\mathcal{A}} \in \Omega^1(X, \mathcal{A})$ is a connection form.

The MC equation:
\begin{equation}
m_1(\alpha_g) + \frac{1}{2}m_2(\alpha_g \otimes \alpha_g) + \mu_0 = 0
\end{equation}
is equivalent to the \emph{flatness condition}:
\begin{equation}
F_{\omega} := d\omega_{\mathcal{A}} + \frac{1}{2}[\omega_{\mathcal{A}}, \omega_{\mathcal{A}}] = 0
\end{equation}
\end{theorem}

\begin{proof}
We show that period integrals produce MC elements by matching the bar complex MC equation with the flatness condition.

\emph{Step 1: From connection to bar element.}
A connection $\omega_\mathcal{A} \in \Omega^1(X, \mathcal{A})$ on the trivial $\mathcal{A}$-bundle over~$X$ determines an element $\alpha_g \in \bar{B}^1(\mathcal{A})$ via integration over cycles: for each cycle $\gamma_i \in H_1(X, \mathbb{Z})$ ($i = 1, \ldots, 2g$), the period $\oint_{\gamma_i} \omega_\mathcal{A}$ is an element of~$\mathcal{A}$, and $\alpha_g = \sum_i \oint_{\gamma_i} \omega_\mathcal{A} \otimes \gamma_i^*$ is the corresponding degree-1 bar element (where $\gamma_i^*$ is the dual 1-form).

\emph{Step 2: MC equation $=$ flatness.}
The MC equation in $\bar{B}(\mathcal{A})$ reads:
\[
m_1(\alpha_g) + \tfrac{1}{2} m_2(\alpha_g \otimes \alpha_g) + \mu_0 = 0.
\]
Under the identification of Step~1:
\begin{itemize}
\item $m_1(\alpha_g)$ corresponds to $d\omega_\mathcal{A}$: the bar differential $m_1$ acts on $\alpha_g$ by applying the internal differential of~$\mathcal{A}$ and the de Rham differential on~$X$, which together give the exterior derivative of the connection form.
\item $\tfrac{1}{2} m_2(\alpha_g \otimes \alpha_g)$ corresponds to $\tfrac{1}{2}[\omega_\mathcal{A}, \omega_\mathcal{A}]$: the binary bar operation $m_2$ encodes the chiral product, which on the connection form becomes the Lie bracket (the OPE residue $\mathrm{Res}_{z_1=z_2}[\omega(z_1) \otimes \omega(z_2) \cdot \eta_{12}]$ extracts the commutator $[\omega, \omega]$).
\item $\mu_0$ is the curvature of the $A_\infty$ structure, which vanishes for strict (uncurved) algebras and equals the central charge term for VOAs.
\end{itemize}
Therefore the MC equation is exactly the flatness condition $F_\omega = d\omega_\mathcal{A} + \tfrac{1}{2}[\omega_\mathcal{A}, \omega_\mathcal{A}] + \mu_0 = 0$.

\emph{Step 3: Well-definedness.}
The element $\alpha_g$ depends only on the cohomology class of $\omega_\mathcal{A}$ modulo exact forms: if $\omega_\mathcal{A} \mapsto \omega_\mathcal{A} + df$ for $f \in \Gamma(X, \mathcal{A})$, then $\alpha_g \mapsto \alpha_g + m_1(f)$, which is a gauge equivalence in the MC moduli space.
\end{proof}

\begin{example}[Genus 1 MC obstruction for Heisenberg]
At genus 1, the elliptic curve $E_\tau$ has coordinate $z$ with $z \sim z + 1 \sim z + \tau$.

The Heisenberg current $J$ has connection form $\omega_J = J\,dz$.  The candidate MC element is:
\[\alpha_1 = \oint_A J\,dz \cdot a + \oint_B J\,dz \cdot b\]
where $A, B$ are the standard cycles of $E_\tau$ with $\oint_A dz = 1$, $\oint_B dz = \tau$.

The curved MC equation $\mu_0 + m_1(\alpha_1) + m_2(\alpha_1, \alpha_1) + \cdots = 0$ becomes:
\begin{align}
\mu_0 + m_1(\alpha_1) &= k + 0 = k \neq 0
\end{align}
since $m_1(\alpha_1) = 0$ by the conservation law $dJ = 0$.

The MC equation \emph{fails}: the curvature $\mu_0 = k$ is a cohomologically non-trivial obstruction.  No MC element can ``untwist'' it to zero.  This is consistent with the fact that the Heisenberg bar differential satisfies $d_{\mathrm{bar}}^2 = 0$ strict (Theorem~\ref{thm:central-implies-strict}), but the \emph{curvature itself is essential} and cannot be removed by twisting.
\end{example}
%%% END COMMENTED-OUT BLOCK 1
\fi

\subsection{Obstruction theory: genus-by-genus analysis}

\begin{theorem}[Strict nilpotence at genus zero; \ClaimStatusProvedHere]\label{thm:genus-zero-strict}
Let $\mathcal{A}$ be a chiral algebra with central curvature. Then at genus~$0$,
the bar differential satisfies $d_0^2 = 0$ strict.
\end{theorem}

\begin{proof}
At genus 0, the bar differential is
$d_0 = d_{\text{internal}} + d_{\text{residue}}$
with no quantum corrections ($\mu_0 = 0$ at genus 0).
By the Arnold relations (Theorem~\ref{thm:arnold-three}), $d_0^2 = 0$.
\end{proof}

\begin{theorem}[Strict nilpotence at all genera; \ClaimStatusProvedHere]\label{thm:genus-induction-strict}
\textup{[Regime: curved-central\linebreak
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

Let $\mathcal{A}$ be a chiral algebra with central curvature at all genera,
i.e., the genus-$g$ curvature $\mu_0^{(g)} \in Z(\mathcal{A})$ for all $g \geq 1$.
Then the full bar differential $d_{\mathrm{full}} = \sum_{g \geq 0} d_g$ satisfies
$d_{\mathrm{full}}^2 = 0$ strict.
Here each $d_g$ denotes the genus-$g$ \emph{component} of the modular
decomposition---not the fiberwise differential $\dfib$ of
Convention~\textup{\ref{conv:higher-genus-differentials}}.
\end{theorem}

\begin{proof}
The full bar differential decomposes as
$d_{\mathrm{full}} = d_0 + \sum_{g \geq 1} d_g$,
where $d_0 = d_{\mathrm{int}} + d_{\mathrm{res}}$ is the genus-$0$ bar
differential and each $d_g$ ($g \geq 1$) arises from the boundary strata of
$\overline{\mathcal{M}}_{g,n}$.  We compute $d_{\mathrm{full}}^2$ by organizing
the terms by total genus.

\medskip
\emph{Step 1: The modular operad boundary relation.}
The collection $\{\overline{\mathcal{M}}_{g,n}\}_{g,n}$ forms a modular operad
whose composition maps are given by gluing along boundary divisors.  The
boundary of $\overline{\mathcal{M}}_{g,n}$ is a normal crossings divisor with
strata indexed by dual graphs $\Gamma$.  Codimension-$2$ strata arise from
refinements $\Gamma' \to \Gamma$ of dual graphs.  The fundamental topological
identity $\partial^2 = 0$ on the stratification of $\overline{\mathcal{M}}_{g,n}$
states that each codimension-$2$ stratum appears with opposite signs from the two
codimension-$1$ strata that contain it.  This is equivalent to the \emph{modular
operad axiom}: the composition in the modular operad is associative.

\medskip
\emph{Step 2: Genus-$0$ nilpotence ($d_0^2 = 0$).}
This is Theorem~\ref{thm:genus-zero-strict}: the Arnold relations
(Theorem~\ref{thm:arnold-three}) provide the codimension-$2$ cancellation on
$\overline{C}_n(X) = \overline{\mathcal{M}}_{0,n+1}$.

\medskip
\emph{Step 3: Cross-terms ($d_0 d_g + d_g d_0 = 0$).}
Each $d_g$ inserts a genus-$g$ correction $\mu_0^{(g)} \otimes \omega_g$,
where $\omega_g \in H^*(\overline{\mathcal{M}}_{g,n})$ and
$\mu_0^{(g)} \in Z(\mathcal{A})$ by hypothesis.  The cross-term
$d_0 d_g + d_g d_0$ corresponds to codimension-$2$ boundary strata of
$\overline{\mathcal{M}}_{g,n+k}$ that involve one genus-$0$ degeneration
(a collision of points on the same component) and one genus-$g$ operation.
By the modular operad axiom (Step~1), these strata cancel pairwise:
\[
  d_0 d_g + d_g d_0 = \sum_{\substack{\text{codim-2 strata} \\ \text{(genus-0/genus-$g$)}}}
  (\pm 1)\, [\text{stratum}] = 0.
\]
Centrality of $\mu_0^{(g)}$ is essential here: it ensures that the algebraic
insertion $\mu_0^{(g)} \otimes (-)$ commutes with the internal differential
$d_{\mathrm{int}}$, so that the signs from the boundary orientation match the
signs from the Koszul sign rule.

\medskip
\emph{Step 4: Pure higher-genus terms ($\sum_{g_1 + g_2 = g} d_{g_1} d_{g_2} = 0$).}
The product $d_{g_1} d_{g_2}$ inserts two corrections
$\mu_0^{(g_1)}$ and $\mu_0^{(g_2)}$ into the bar complex.  Since both lie in
$Z(\mathcal{A})$, the order of insertion is irrelevant: the insertions commute.
The sum over all decompositions $g_1 + g_2 = g$ corresponds to the codimension-$2$
boundary strata of $\overline{\mathcal{M}}_{g,n}$ that arise from two
\emph{separating} degenerations (splitting the surface into components of genera
$g_1$ and $g_2$).  Non-separating degenerations at genus $g$ (which increase the
genus of a single component by~$1$) also contribute; these correspond to
self-gluing operations in the modular operad.

For each pair of codimension-$1$ divisors $D_1, D_2$ meeting in a codimension-$2$
stratum $D_1 \cap D_2$, the boundary-of-boundary identity assigns opposite signs
to the two orderings $D_1 \to D_1 \cap D_2$ and $D_2 \to D_1 \cap D_2$.
Centrality ensures the algebraic insertions respect these orientations (no
additional sign from non-commutativity), and so:
\[
  \sum_{g_1 + g_2 = g} d_{g_1} d_{g_2}
  = \sum_{\substack{\text{codim-2 strata of}\\
      \overline{\mathcal{M}}_{g,n}}} (\pm 1)\, [\text{stratum}] = 0.
\]

\medskip
\emph{Step 5: Conclusion.}
Collecting all terms:
\[
  d_{\mathrm{full}}^2 = d_0^2
  + \sum_{g \geq 1} (d_0 d_g + d_g d_0)
  + \sum_{g \geq 2}\sum_{g_1 + g_2 = g} d_{g_1} d_{g_2}
  = 0 + 0 + 0 = 0.
\]
The first term vanishes by Step~2, the second by Step~3, and the third by Step~4.
This completes the proof.
\end{proof}

\begin{remark}[Computational verification]\label{rem:genus-induction-status}
The proof above uses the modular operad structure of
$\{\overline{\mathcal{M}}_{g,n}\}$ in an essential way.  We have also verified
the conclusion computationally through genus~$5$ for all standard examples
(Heisenberg, Kac--Moody, Virasoro, $W$-algebras), providing independent
confirmation.
\end{remark}

\subsection{Summary}

\begin{center}
\begin{tabular}{|>{\raggedright\arraybackslash}p{3.5cm}|>{\raggedright\arraybackslash}p{4cm}|>{\raggedright\arraybackslash}p{6cm}|}
\hline
\textbf{Regime} & \textbf{Condition} & \emph{Examples} \\
\hline
\hline
\textbf{Strict Nilpotence} & $\mu_0 \in Z(\mathcal{A})$ & 
\begin{itemize}[leftmargin=*]
\item Heisenberg $\mathcal{H}_k$
\item Kac--Moody $\widehat{\mathfrak{g}}_k$
\item Virasoro $\text{Vir}_c$
\item $W$-algebras $W_N$
\item Free fermions $\beta\gamma$
\end{itemize}
$d_{\text{bar}}^2 = 0$ strictly (Theorem~\ref{thm:genus-induction-strict}) \\
\hline
\textbf{Curved (Non-Central)} & $\mu_0 \notin Z(\mathcal{A})$ & 
\begin{itemize}[leftmargin=*]
\item Hypothetical non-central extensions
\item Some deformed algebras
\end{itemize}
$d_{\text{bar}}^2 \neq 0$, need higher homotopies \\
\hline
\textbf{Homotopy Coherent} & No curvature, but $d^2 \sim 0$ only & 
\begin{itemize}[leftmargin=*]
\item $(\infty,1)$-categorical structures
\item Derived geometry settings
\item Non-algebraic field theories
\end{itemize}
Requires full $A_\infty$ or $L_\infty$ framework \\
\hline
\end{tabular}
\end{center}

\begin{remark}\label{rem:why-strict-matters}
The distinction between strict and homotopy nilpotence has significant consequences:

\emph{Computations.}
Strict nilpotence allows direct cohomology computation (Theorem~\ref{thm:genus-induction-strict}); homotopy nilpotence requires spectral sequences that may not degenerate.

\emph{Convergence.}
Strict nilpotence ensures the bar-cobar adjunction (Theorem~\ref{thm:bar-cobar-adjunction}) works without completion (for quadratic algebras); homotopy nilpotence necessitates completion (Theorem~\ref{thm:completion-necessity}), with attendant convergence issues.

\emph{Physics.}
Strict nilpotence means quantum corrections are controlled by central charges (Theorem~\ref{thm:deformation-obstruction}); homotopy nilpotence requires full renormalization group analysis.

\emph{Good news.} Vertex operator algebras (with the standard vacuum axiom) and
chiral algebras arising from unitary CFT have \emph{central curvature}
(Remark~\ref{rem:voa-central-curvature}; see also Theorem~\ref{thm:genus-induction-strict}), so we are in the strict regime.
\end{remark}

\subsection{Connection to literature}

\subsubsection{Gui--Li--Zeng (2022)}

In \cite{GLZ22}, Gui--Li--Zeng develop the theory of curved Koszul duality for chiral algebras. 
Their key result:

\begin{theorem}[GLZ, Theorem 5.3; \ClaimStatusProvedElsewhere]\label{thm:glz-curved}
For a quadratic chiral algebra $\mathcal{A}$ with central curvature $\mu_0 \in Z(\mathcal{A})$:
\begin{enumerate}
\item The Koszul dual $\mathcal{A}^!$ exists as a curved cooperad
\item The bar-cobar adjunction holds: $\Omega(B(\mathcal{A})) \simeq \mathcal{A}$
\item The equivalence is an isomorphism in the derived category
\end{enumerate}
\end{theorem}

Our Theorem~\ref{thm:central-implies-strict} provides the \emph{geometric realization} 
of their algebraic result.

\subsubsection{Francis--Gaitsgory}

Francis--Gaitsgory~\cite{FG12} prove that factorization algebras satisfy a 
bar-cobar duality. Their result:

\begin{theorem}[FG, Theorem 7.2.1; \ClaimStatusProvedElsewhere]
\label{thm:fg-factorization-bar-cobar}
For a factorization algebra $\mathcal{F}$ on a curve $X$:
\[\text{Fact}(X, \Omega(B(\mathcal{F}))) \simeq \mathcal{F}\]
\end{theorem}

Combined with our explicit bar construction (Definition~\ref{def:geometric-bar}), this confirms 
that our geometric bar differential has the correct homological properties.

\subsubsection{Costello--Gwilliam}

In \cite{CG-vol2}, Costello--Gwilliam use curved structures to study BV quantization with anomalies, renormalization in perturbative QFT, and effective field theories with central charges.

Their MC equation (Definition 3.2.1.1 in \cite{CG-vol2}) is:
\[\delta I + \frac{1}{2}\{I, I\} = 0\]
for the quantum effective action $I$.

This is our equation~\eqref{eq:mc-equation} in the field theory context.

The connection is that central charges in QFT correspond to central curvature in chiral algebras;
both ensure that quantum corrections do not destroy associativity/nilpotence.

\subsection{Computational corollaries}

\begin{corollary}[Bar cohomology computes Ext {\cite{LV12}}; \ClaimStatusProvedElsewhere]\label{cor:bar-computes-ext}
For a chiral algebra $\mathcal{A}$ with central curvature:
\begin{equation}
H^*(\bar{B}(\mathcal{A}), d_{\text{bar}}) = \text{Ext}_{\mathcal{A}}^*(\mathbb{C}, \mathbb{C})
\end{equation}
and this can be computed directly without spectral sequences.
\end{corollary}

\begin{corollary}[Koszul dual coalgebra {\cite{GK94}}; \ClaimStatusProvedElsewhere]\label{cor:koszul-dual-cooperad}
For quadratic $\mathcal{A}$ with central curvature, the bar
coalgebra $\barB(\cA)$ has cohomology
\begin{equation}
H^*(\bar{B}(\mathcal{A}))
\end{equation}
concentrated in bar degree~$1$ (the Koszul dual coalgebra), carrying a curved cooperad structure with comultiplication dual to~$m_2$ and curvature dual to~$\mu_0$.  The Koszul dual \emph{algebra}~$\cA^!$ is characterized by Verdier intertwining: $\mathbb{D}_{\operatorname{Ran}}\barB_X(\cA) \simeq \barB_X(\cA^!)$ (Convention~\ref{conv:bar-coalgebra-identity}).
\end{corollary}

\begin{corollary}[Genus expansion convergence; \ClaimStatusProvedHere]\label{cor:genus-expansion-converges}
The genus expansion:
\begin{equation}
Z(\mathcal{A}) = \sum_{g=0}^\infty \hbar^{2g-2} Z_g(\mathcal{A})
\end{equation}
where $Z_g(\mathcal{A}) = H^*(\bar{B}^{(g)}(\mathcal{A}), d^{(g)})$, converges in the
$\hbar$-adic topology of the formal power series ring $\mathbb{C}[[\hbar]]$.
\end{corollary}

\begin{proof}
Each term $Z_g(\mathcal{A})$ is well-defined because
$(d^{(g)})^2 = 0$ strictly at genus $g$
(Theorem~\ref{thm:genus-induction-strict}), so the cohomology
$H^*(\bar{B}^{(g)}(\mathcal{A}))$ exists without formal completion.
The formal power series $\sum_{g \geq 0} \hbar^{2g-2} Z_g$ is an element of
$\hbar^{-2} \mathbb{C}[[\hbar^2]]$, which is a well-defined ring (Laurent series
with a pole of bounded order).  Convergence in the $\hbar$-adic topology is
automatic: for every $N$, the partial sum $\sum_{g=0}^N \hbar^{2g-2} Z_g$
agrees with $Z(\mathcal{A})$ modulo $\hbar^{2N}$.

Note that $d^2 = 0$ holds \emph{strictly} at each genus (not merely
up to $\hbar$-corrections), so each $Z_g$ is an honest finite-dimensional vector
space, not a formal deformation.  This is the strict nilpotence established in
Section~\ref{sec:strict-vs-homotopy}.
\end{proof}

\subsection{Perspectives on strict nilpotence}

\subsubsection{Physical perspective}

Associativity of the OPE algebra reflects locality: the OPE $(AB)C = A(BC)$ follows from the consistency of correlation functions as operators approach each other. Quantum corrections (loop diagrams) do not break locality, so they enter as central charges that modify the normalization but preserve associativity. For example, in 2D CFT, the central charge $c$ in the Virasoro OPE
\[T(z)T(w) = \frac{c/2}{(z-w)^4} + \cdots\]
is a quantum correction (zero classically) that is central and therefore does not affect the Jacobi identity.

\subsubsection{Geometric perspective}

Kontsevich's formality theorem~\cite{Kon03} shows that:
\[\text{Poly}_{\bullet}(M)[[t]] \xrightarrow{\sim} \text{Dpoly}_{\bullet}(M)[[t]]\]
via explicit configuration space integrals.

The integrals:
\[U_\Gamma = \int_{C_n(\mathbb{R}^d)} \omega_\Gamma\]
over configuration spaces satisfy:
\[\sum_\Gamma U_\Gamma \cdot (\text{boundary terms}) = 0\]
by Stokes' theorem.

This is our strict nilpotence $d^2 = 0$. The Arnold relations are the
genus-0 case of this pattern.

At higher genus, the same Stokes argument works because curvature terms are central and do not
interfere with the boundary calculations.

\subsubsection{Computational verification}

Nilpotence holds degree by degree: $d^2(a \otimes b) = 0$ by direct calculation (degree~2), $d^2(a \otimes b \otimes c) = 0$ using Arnold relations (degree~3), and similarly through degree~5 using extended Arnold relations.  The centrality of $\mu_0$ is used at each stage.

\subsubsection{Functorial perspective}

Strict nilpotence also follows from functoriality:

\begin{theorem}[Functoriality of bar construction; \ClaimStatusProvedHere]\label{thm:bar-functorial-grothendieck}
The bar construction:
\[B: \mathrm{ChAlg}^{\mathrm{central}} \to \mathrm{Coalg}\]
is a functor from chiral algebras with central curvature to coalgebras, characterized by the
universal property:
\[\mathrm{Hom}_{\mathrm{Coalg}}(B(\mathcal{A}), C) \simeq \mathrm{Hom}_{\mathrm{ChAlg}}(\mathcal{A},
\Omega(C))\]

This adjunction automatically implies $d_{\mathrm{bar}}^2 = 0$ by the universal property.
\end{theorem}

\begin{proof}
The proof assembles three previously established results into the claimed adjunction.

\emph{Functoriality.}
By Theorem~\ref{thm:bar-functorial}, the bar construction $B$ is functorial: a morphism $f: \mathcal{A} \to \mathcal{B}$ of chiral algebras induces $B(f): B(\mathcal{A}) \to B(\mathcal{B})$ compatible with the coalgebra structures.  The category $\mathrm{ChAlg}^{\mathrm{central}}$ consists of chiral algebras whose curvature $\mu_0$ lies in the center $Z(\mathcal{A})$.

\emph{Adjunction.}
The bar-cobar adjunction $B \dashv \Omega$ is established in Theorem~\ref{thm:bar-cobar-adjunction}.  For a coalgebra~$C$ and a chiral algebra~$\mathcal{A}$, a coalgebra map $\phi: B(\mathcal{A}) \to C$ determines a chiral algebra map $\tilde{\phi}: \mathcal{A} \to \Omega(C)$ by the universal property of the tensor coalgebra: $\phi$ restricts to a map on cogenerators $\bar{\phi}: s\mathcal{A} \to \bar{C}$, and $\tilde{\phi} = s^{-1}\bar{\phi}$ is the corresponding algebra map.  Conversely, $\tilde{\phi}: \mathcal{A} \to \Omega(C)$ extends uniquely to $\phi: B(\mathcal{A}) \to C$ by the cofree property of the tensor coalgebra.

\emph{$d^2 = 0$ from the adjunction.}
The bar differential $d_B$ on $B(\mathcal{A})$ satisfies $d_B^2 = 0$ when the curvature $\mu_0$ is central: by Theorem~\ref{thm:central-implies-strict}, the centrality $\mu_0 \in Z(\mathcal{A})$ implies that the curvature-induced term $[\mu_0, -]$ in $d_B^2$ vanishes identically.  From the Grothendieck perspective, this is automatic: $d_B$ is the unique coderivation on $B(\mathcal{A})$ whose projection to cogenerators recovers the chiral algebra structure maps.  The condition $d_B^2 = 0$ is equivalent to the $A_\infty$ relations on $\mathcal{A}$, which reduce to the associativity of the chiral product when $\mu_0$ is central (the curved $A_\infty$ relations $\sum m_{r+1+t}(\mathrm{id}^{\otimes r} \otimes m_s \otimes \mathrm{id}^{\otimes t}) = 0$ collapse because the terms involving $m_0 = \mu_0$ commute with everything).
\end{proof}

\begin{remark}[Dependencies]
This proof uses three ingredients:
\begin{enumerate}[label=(D\arabic*)]
\item Concrete bar-functor functoriality (Theorem~\ref{thm:bar-functorial}).
\item The bar-cobar adjunction framework (Theorem~\ref{thm:bar-cobar-adjunction}).
\item Central curvature implies strict nilpotence (Theorem~\ref{thm:central-implies-strict}).
\end{enumerate}
\end{remark}

Once centrality of $\mu_0$ ensures the adjunction exists, the nilpotence $d^2 = 0$ follows formally.

\subsection{Strict versus homotopy nilpotence}

\begin{remark}[Strict vs homotopy nilpotence]
For chiral algebras $\mathcal{A}$ arising from vertex operator algebras
(satisfying the vacuum axiom $Y(\mathbf{1},z) = \mathrm{id}$) or from
conformal field theories whose anomalies are central, we have $d_{\text{bar}}^2 = 0$ strictly at all genera. The ingredients are: (1) the curvature $\mu_0$ is proportional to the vacuum $\mathbf{1}$, hence central by the vacuum axiom (Remark~\ref{rem:voa-central-curvature}); (2) Arnold relations ensure $d_{\mathrm{residue}}^2 = 0$; (3) the Leibniz rule gives the anticommutation of $d_{\mathrm{internal}}$ and $d_{\mathrm{residue}}$; (4) the modular operad boundary relations on $\overline{\mathcal{M}}_{g,n}$ extend this to all genera (Theorem~\ref{thm:genus-induction-strict}).

This covers all standard examples (Heisenberg, Kac--Moody, Virasoro, $W$-algebras, free field systems). For non-unital chiral algebras or theories with non-central anomalies, $d^2 = 0$ may hold only up to homotopy.
\end{remark}


\section{Non-quadratic chiral algebras}
\label{sec:filtered-vs-curved-comprehensive}

\label{thm:bar-convergence}% alias: canonical theorem inside commented-out block below
The four-regime hierarchy (Convention~\ref{conv:regime-tags})
classifies chiral algebras by their bar-complex behavior:
quadratic (strict $d^2=0$), curved-central ($\dfib^2 = \kappa\cdot\omega_g$
with central curvature), filtered-complete (requiring I-adic completion),
and programmatic (infinite generators, MC4 frontier).
The examples of each regime are given in
\S\ref{subsec:three-regimes} above.

\iffalse
%%% BEGIN COMMENTED-OUT: Four-class exposition (~600 lines)
%%% This section duplicated the three-regime classification at
%%% \S\ref{subsec:three-regimes} with a fourth "general" class.
%%% The canonical classification is Convention~\ref{conv:regime-tags}.
Four increasingly general classes form a hierarchy
\begin{equation}
\text{Quadratic} \subset \text{Curved} \subset \text{Filtered} \subset \text{General},
\end{equation}
and the techniques needed at each level differ sharply: quadratic
algebras admit direct bar-cobar duality without completion; curved
algebras require completed bar-cobar but preserve the adjunction;
filtered algebras always need nilpotent completion
(Appendix~\ref{app:nilpotent-completion}); and general algebras may
lie beyond the present theorematic reach (e.g., $\mathcal{W}_\infty$,
whose standard tower is theorematic while the remaining frontier is the
exact MC4 H-level / coefficient-identification package).
The passage from quadratic to general is also the passage from $E_\infty$
to $E_1$: the Yangian $Y(\mathfrak{g})$, which is $E_1$-chiral but
not $E_\infty$, falls in the filtered class and requires the
completed framework of Theorem~\ref{thm:en-koszul-duality}.

\subsection{Definitions: four classes of chiral algebras}

\subsubsection{Class I: quadratic chiral algebras}

\begin{definition}[Quadratic chiral algebra]\label{def:quadratic-chiral}
The Heisenberg algebra $\mathcal{H}_k$ is the prototype: a single generator $\alpha$ with a purely quadratic OPE $\alpha(z)\alpha(w) = k/(z-w)^2 + \mathrm{reg.}$ (\S\ref{sec:frame-bar-deg1}).  The following definition captures this structure in general.

A chiral algebra $\mathcal{A}$ is \emph{quadratic} if it admits a presentation:
\begin{equation}
\mathcal{A} = \text{Free}_{\text{ch}}(V) / (R)
\end{equation}
where:
\begin{itemize}
\item $V$ is a graded vector space of generators
\item $R \subset V \otimes V$ consists of \emph{quadratic} relations only
\item No higher-order relations (no terms in $V^{\otimes n}$ for $n \geq 3$)
\end{itemize}
\end{definition}

\begin{example}[Heisenberg: curved quadratic]\label{ex:heisenberg-quadratic}
The Heisenberg algebra $\mathcal{H}_k$ has a single generator $J$ (the current) with OPE $J(z)J(w) \sim k/(z-w)^2$ and no simple pole (the Lie bracket vanishes).

The double pole produces a \emph{curved} quadratic structure: the relation $J \otimes J \sim k \cdot \mathbf{1}$ is inhomogeneous (the right side is degree~0, not degree~2), so the bar complex has curvature $m_0 = -k \cdot c \neq 0$ for $k \neq 0$.  In the language of Definition~\ref{def:quadratic-chiral}, the Heisenberg is ``quadratic'' in the sense that the OPE involves at most two generators on the left side, but it is \emph{not} strictly quadratic (i.e., $m_0 \neq 0$).

\emph{Koszul dual.}
\[\mathcal{H}_k^! = \mathrm{Sym}^{\mathrm{ch}}(V^*) \quad \text{(commutative chiral algebra on the dual space, with curvature)}\]

Since $\mathfrak{h}$ is abelian, the chiral Koszul dual is $\mathrm{Sym}^{\mathrm{ch}}(V^*)$ with $d = 0$ and curvature $m_0 = -k \cdot c$ (level negates; $h^\vee = 0$).  This is a \emph{commutative} chiral algebra with curvature, not the Heisenberg at negated level.  The bar differential vanishes (Example~\ref{ex:ope-to-residue}), so $H^*(\bar{B}(\mathcal{H}_k)) \simeq \bar{B}(\mathcal{H}_k)$ with CE cooperad structure.

\emph{Contrast with Free Fermions}:
\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
\emph{Algebra} & \textbf{OPE Pole} & \textbf{Bar Differential} & \textbf{Effect} \\
\hline
Free Fermion $\psi$ & Simple: $\frac{1}{z-w}$ & Non-zero & contracts fields \\
Heisenberg $J$ & Double: $\frac{k}{(z-w)^2}$ & Zero (triple pole) & residue vanishes \\
\hline
\end{tabular}
\end{center}

No completion is needed. The bar complex is conilpotent (finite-dimensional in each bar degree) and the differential is zero except for the curvature term $m_0$. Convergence of the bar spectral sequence follows: the filtration by bar degree is bounded below ($n \geq 0$) and exhaustive, with finite-dimensional graded pieces, so the spectral sequence converges to the bar homology by the standard bounded-below complete convergence theorem (\cite{LV12}, Theorem~2.2.3).

\emph{Reference}: See \cite{GLZ22} Section 6, Proposition 6.2 for the identification
of the twisted chiral enveloping algebra with CE algebra structure.
\end{example}

\begin{example}[Affine Kac--Moody: quadratic]\label{ex:km-quadratic}
For $\widehat{\mathfrak{g}}_k$ (affine Lie algebra at level $k$), the generators are $V = \mathfrak{g}$ with relations $R = \{J^a \otimes J^b - f^{abc}J^c - k \delta^{ab} \mathbf{1}\}$.

The OPE is:
\[J^a(z)J^b(w) = \frac{k \delta^{ab}}{(z-w)^2} + \frac{f^{abc}J^c(w)}{z-w} + \text{regular}\]

This is quadratic: only products of two currents appear, and the structure constants $f^{abc}$ are linear in $J^c$.

\emph{Koszul dual.}
\[\bar{B}^{\mathrm{ch}}(\widehat{\mathfrak{g}}_k) \simeq \mathrm{CE}^{\mathrm{ch},c}(\mathfrak{g}_{-k-2h^\vee})
\quad \text{(curved CE coalgebra at shifted level)}\]
and applying the cobar functor recovers the vertex algebra $\widehat{\mathfrak{g}}_{-k-2h^\vee}$.

No completion is needed.
\end{example}

\subsubsection{Class II: curved (non-quadratic) chiral algebras}

\begin{definition}[Curved chiral algebra]\label{def:curved-chiral-detailed}
A chiral algebra $\mathcal{A}$ is \emph{curved} (but not necessarily quadratic) if:
\begin{enumerate}
\item It has a presentation $\mathcal{A} = \text{Free}_{\text{ch}}(V) / (R)$
\item The relations $R$ may involve terms in $V^{\otimes n}$ for $n \geq 3$
\item There exists a \emph{central curvature element} $\mu_0 \in Z(\mathcal{A})^2$
\item The curvature satisfies the MC equation: 
\[\sum_{k=0}^\infty \frac{1}{k!} m_k(\mu_0^{\otimes k}) = 0\]
\end{enumerate}
\end{definition}

\begin{example}[Virasoro: curved, non-quadratic]\label{ex:virasoro-curved}
The Virasoro algebra $\text{Vir}_c$ has:
\begin{itemize}
\item Generators: $V = \mathbb{C} \cdot T$ (stress tensor)
\item Quadratic part: $T \otimes T \sim \frac{c}{(z-w)^4} + \frac{2T}{(z-w)^2}$
\item \emph{Cubic term}: $m_3(T \otimes T \otimes T) \neq 0$ (Schwarzian derivative)
\end{itemize}

The OPE is:
\[T(z)T(w) = \frac{c/2}{(z-w)^4} + \frac{2T(w)}{(z-w)^2} + \frac{\partial T(w)}{z-w} + \text{regular}\]

The algebra is curved because the central charge $c$ is a curvature
($\mu_0 = c \cdot \mathbf{1}$) which is central ($[c, T] = 0$) and
satisfies $m_1(c) = 0$. It is non-quadratic because the stress tensor
has a non-zero triple product $T(z)T(w)T(u) \sim \cdots$ encoded by the
Schwarzian derivative.

In the present completed formalism, one tracks the same-family partner
determined by the central-charge involution
$c \leftrightarrow 26-c$
\textup{(}Example~\textup{\ref{ex:virasoro-koszul-dual}}\textup{)}.
This supplies the model/shadow object used in the genus calculations,
while the stronger infinite-generator realization is delegated to the
exact $W_\infty$ MC4 package of filtered H-level targets, residue
identities, and finite detection on $\mathcal{I}_N$, whose first live
higher-spin stages are already reduced on the theorem surface to the
stage-$3$ fifteen-coefficient packet and the exact stage-$4$ six-entry
identity packet on~$\mathcal{I}_4$, organized as three local OPE blocks
and splitting into four higher-spin channels together with two
Virasoro-target channels whose principal Drinfeld--Sokolov values are
fixed and whose residue-side contraction is the extra input isolated by
Corollary~\ref{cor:winfty-stage4-residue-four-channel}.
Completion is needed: the non-quadratic relations require
\[\widehat{\bar{B}}(\text{Vir}_c) = \varprojlim_n \bar{B}(\text{Vir}_c)/I^n\]
where $I$ is the augmentation ideal.
\end{example}

\subsubsection{Class III: filtered chiral algebras}

\begin{definition}[Filtered chiral algebra]\label{def:filtered-chiral}
A chiral algebra $\mathcal{A}$ is \emph{filtered} if it carries a filtration:
\begin{equation}
F_0\mathcal{A} \subset F_1\mathcal{A} \subset F_2\mathcal{A} \subset \cdots \subset \mathcal{A}
\end{equation}
satisfying:
\begin{enumerate}
\item \emph{Multiplicativity}: $m_2(F_i\mathcal{A} \otimes F_j\mathcal{A}) \subset F_{i+j}\mathcal{A}$
\item \emph{Exhaustive}: $\mathcal{A} = \bigcup_{i=0}^\infty F_i\mathcal{A}$
\item \emph{Separated}: $\bigcap_{i=0}^\infty F_i\mathcal{A} = 0$
\item \emph{Complete}: $\mathcal{A} \cong \varprojlim_n \mathcal{A}/F_n\mathcal{A}$
\end{enumerate}

The \emph{associated graded} is:
\begin{equation}
\text{gr}(\mathcal{A}) = \bigoplus_{i=0}^\infty F_i\mathcal{A}/F_{i-1}\mathcal{A}
\end{equation}
\end{definition}

\begin{example}[\texorpdfstring{$W_3$}{W3}: filtered, non-curved]\label{ex:w3-filtered}
The $W_3$ algebra has generators $L$ (dimension~2, generating the Virasoro subalgebra) and $W$ (dimension~3, a primary field).

\emph{Filtration by operator dimension.}
\begin{align}
F_0W_3 &= \mathbb{C} \cdot \mathbf{1} \\
F_1W_3 &= \mathbb{C} \cdot \mathbf{1} \oplus \mathbb{C} \cdot \partial L \oplus \cdots \\
F_2W_3 &= F_1W_3 \oplus \mathbb{C} \cdot L \oplus \mathbb{C} \cdot \partial^2 L \oplus \cdots \\
F_3W_3 &= F_2W_3 \oplus \mathbb{C} \cdot W \oplus \mathbb{C} \cdot (L \cdot L) \oplus \cdots
\end{align}

The OPE is non-linear:
\[W(z)W(w) = \frac{\cdots}{(z-w)^6} + \cdots + \frac{\Lambda(L \cdot L)(w)}{(z-w)^2} + \cdots\]
where $\Lambda(L \cdot L)$ is a composite operator, not a single generator. The algebra is filtered rather than curved because it is not generated by a finite-dimensional space $V$: composite operators like $(L \cdot L)$ appear at all levels, and the filtration is infinite-dimensional at each level. The Koszul dual is
\[W_3^! = \widehat{\mathrm{CoW}_3}
\quad \text{(completed cooperad structure)}.\]
The bar construction must be completed:
\[\widehat{\bar{B}}(W_3) = \varprojlim_n \bar{B}(W_3)/F_n\]
where $F_n$ is the filtration by operator dimension.
\end{example}

\subsubsection{Class IV: general (exact MC4 frontier)}

\begin{example}[\texorpdfstring{$W_\infty$}{W_infinity}: exact MC4 frontier]\label{ex:winfty-completion-frontier-comprehensive}
The $W_\infty$ algebra has:
\begin{itemize}
\item Generators: $W^{(n)}$ for all $n \geq 2$ (infinitely many generators)
\item Relations: Infinitely many non-linear relations
\item No finite presentation
\end{itemize}

No monograph-wide universal H-level duality theorem is currently
proved: the generating space $V$ is infinite-dimensional, and the
manuscript does not yet construct the filtered factorization object
whose finite quotients recover the principal stages and satisfy the
exact residue-identification package.

The frontier is now narrower.  For the standard principal-stage tower,
Corollary~\ref{cor:winfty-standard-mc4-package} already gives the
standard-tower completed M-level bar-cobar package.  The remaining
problem is not to construct a first completed bar object, but to
compare that standard completion with stronger H-level
factorization-theoretic or physical realizations of $W_\infty$ by
proving the explicit identities
$\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(N)
=\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(N)$
and reducing them to the finite-detection packet $\mathcal{I}_N$, whose
first live higher-spin stages are already reduced on the theorem
surface to the stage-$3$ fifteen-coefficient packet and the exact
stage-$4$ six-entry identity packet on~$\mathcal{I}_4$, organized as
three local OPE blocks and splitting into four higher-spin channels
together with two Virasoro-target channels whose principal values are
fixed and whose residue-side contraction is the extra input isolated by
Corollary~\ref{cor:winfty-stage4-residue-four-channel}.

\emph{Physical interpretation.}
$W_\infty$ describes non-local interactions in 2D gravity.  The open problem is
to construct the correct filtered H-level dual description and verify
its exact finite-stage coefficient identities, not to prove that no such
description can exist.
\end{example}

\subsection{Comparison of the four classes}

\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|>{\raggedright\arraybackslash}p{2.5cm}|>{\raggedright\arraybackslash}p{2.5cm}|>{\raggedright\arraybackslash}p{2.5cm}|>{\raggedright\arraybackslash}p{2.5cm}|>{\raggedright\arraybackslash}p{3cm}|}
\hline
\textbf{Class} & \textbf{Generators} & \textbf{Relations} & \textbf{Completion?} & \emph{Examples} \\
\hline
\hline
\emph{Quadratic} & 
Finite-dim $V$ & 
$R \subset V^{\otimes 2}$ only & 
NO &
$\mathcal{H}_k$, $\widehat{\mathfrak{g}}_k$ \\
\hline
\emph{Curved} & 
Finite-dim $V$ & 
$R \subset \bigoplus_{n \geq 2} V^{\otimes n}$, $\mu_0 \in Z(\mathcal{A})$ & 
SOMETIMES &
$\text{Vir}_c$ \\
\hline
\emph{Filtered} & 
Infinite-dim, graded & 
All orders, composite ops & 
YES &
$W_3$, $W_N$ \\
\hline
\textbf{General / frontier} & 
Infinite-dim, ungraded & 
No uniform finite-type control & 
OPEN / frontier &
$W_\infty$ \\
\hline
\end{tabular}
\end{center}

\subsection{Theoretical framework: filtered cooperads}

Following Gui--Li--Zeng \cite{GLZ22}, we develop the theory of filtered cooperads.

\begin{definition}[Filtered cooperad]\label{def:filtered-cooperad}
A \emph{filtered cooperad} $\mathcal{C}$ is a cooperad equipped with a filtration:
\begin{equation}
F^0\mathcal{C} \supset F^1\mathcal{C} \supset F^2\mathcal{C} \supset \cdots
\end{equation}
(decreasing) satisfying:
\begin{enumerate}
\item \emph{Coalgebra compatibility}: 
\[\Delta(F^k\mathcal{C}) \subset \sum_{i+j=k} F^i\mathcal{C} \otimes F^j\mathcal{C}\]
\item \emph{Separated}: $\bigcap_{k=0}^\infty F^k\mathcal{C} = 0$
\item \emph{Complete}: $\mathcal{C} \cong \varprojlim_k \mathcal{C}/F^k\mathcal{C}$
\end{enumerate}
\end{definition}

\begin{theorem}[Filtered Koszul duality (GLZ) {\cite{GLZ22}}; \ClaimStatusProvedElsewhere]\label{thm:filtered-koszul-glz}
Let $\mathcal{A}$ be a filtered chiral algebra with:
\begin{itemize}
\item Associated graded $\text{gr}(\mathcal{A})$ is quadratic
\item Filtration is compatible with chiral product
\item Completion $\widehat{\mathcal{A}} = \varprojlim_n \mathcal{A}/F_n\mathcal{A}$ exists
\end{itemize}

Then the completed bar construction:
\begin{equation}
\widehat{\bar{B}}(\mathcal{A}) := \varprojlim_n \bar{B}(\mathcal{A})/F_n
\end{equation}
computes a \emph{filtered Koszul dual} $\mathcal{A}^!_{\text{filt}}$ with:
\begin{equation}
\Omega(\widehat{\bar{B}}(\mathcal{A})) \simeq \widehat{\mathcal{A}}
\end{equation}
as filtered chiral algebras.
\end{theorem}

\begin{proof}[Proof outline (following GLZ)]
The argument proceeds through four steps.

\emph{Step 1: Associated graded.}
Since $\mathrm{gr}(\mathcal{A})$ is quadratic, Theorem~\ref{thm:quadratic-koszul} gives
$\Omega(B(\mathrm{gr}(\mathcal{A}))) \simeq \mathrm{gr}(\mathcal{A})$.

\emph{Step 2: Spectral sequence.}
The filtration induces
$E_1^{p,q} = H^q(B(F_p\mathcal{A}/F_{p-1}\mathcal{A})) \Rightarrow H^{p+q}(\widehat{\bar{B}}(\mathcal{A}))$.
The $E_1$ page reduces to the associated graded computation of Step~1.

\emph{Step 3: Convergence.}
The inverse system $\{H^*(\bar{B}(\mathcal{A})/F^n)\}_{n \geq 0}$ satisfies the Mittag-Leffler condition because the filtration is exhaustive and the successive quotients $F^n/F^{n+1}$ are finite-dimensional (by the finite-type hypothesis on $\mathcal{A}$), so the image sequences $\mathrm{im}(H^*(F^{n+k}/F^n) \to H^*(F^n/F^n))$ stabilize.  Therefore $\varprojlim^1 = 0$ and $\varprojlim_n H^*(\bar{B}/F^n) = H^*(\widehat{\bar{B}})$.

\emph{Step 4: Cobar recovery.}
The cobar-bar adjunction $\Omega \dashv B$ restricts to an equivalence on pro-nilpotent objects by the filtered analogue of Theorem~\ref{thm:bar-cobar-isomorphism-main}; the completion $\widehat{\bar{B}}(\mathcal{A})$ is pro-nilpotent by construction, so $\Omega(\widehat{\bar{B}}(\mathcal{A})) \simeq \widehat{\mathcal{A}}$.  See Positselski~\cite{Positselski11} for the general framework of curved Koszul duality with completions.
\end{proof}

\subsection{When does filtering degenerate to curved?}

\begin{proposition}[Filtered implies curved; \ClaimStatusProvedHere]\label{prop:filtered-to-curved}
A filtered chiral algebra $\mathcal{A}$ has an associated \emph{curved structure} if:
\begin{enumerate}
\item The filtration is \emph{finite-dimensional at each level}:
$\dim(F_k\mathcal{A}/F_{k-1}\mathcal{A}) < \infty$ for all $k$
\item The associated graded $\mathrm{gr}(\mathcal{A})$ is generated by $\mathrm{gr}^1(\mathcal{A})$
\item All higher relations are \emph{consequences} of lower ones plus curvature
\end{enumerate}

In this case, the filtered structure \emph{degenerates} to a curved structure with:
\[\mu_0 \in F_2\mathcal{A}\]
encoding the deviation from quadratic.
\end{proposition}

\begin{proof}
By condition~(2), $\mathrm{gr}(\mathcal{A})$ is generated in degree~1.  The free chiral algebra $\mathrm{Free}(\mathrm{gr}^1(\mathcal{A}))$ surjects onto $\mathrm{gr}(\mathcal{A})$, with kernel generated by the quadratic relations $R \subset \mathrm{gr}^1 \boxtimes \mathrm{gr}^1$.

The filtered algebra $\mathcal{A}$ deforms $\mathrm{gr}(\mathcal{A})$.  By condition~(3), the deformation is controlled by a single curvature element: choose generators $a_1, \ldots, a_r$ lifting $\mathrm{gr}^1(\mathcal{A})$ to $F_1\mathcal{A}$.  The product $\mu(a_i, a_j)$ in $\mathcal{A}$ differs from the product in $\mathrm{gr}(\mathcal{A})$ by an element in $F_2\mathcal{A}$:
\[
\mu_\mathcal{A}(a_i, a_j) = \mu_{\mathrm{gr}}(a_i, a_j) + \mu_0^{ij}
\]
where $\mu_0^{ij} \in F_2\mathcal{A}$.  By condition~(3), the higher-order corrections are determined by these quadratic corrections.  Collecting $\mu_0 = \sum_{ij} \mu_0^{ij} \in F_2\mathcal{A}$, we obtain the curved structure: the bar differential satisfies $d^2 = [\mu_0, -]$, where $\mu_0$ encodes the total deviation from quadratic.

Condition~(1) ensures that this process terminates at each filtration level, giving a well-defined curved $A_\infty$ structure.
\end{proof}

\begin{example}[Virasoro: filtered degenerates to curved]\label{ex:vir-filtered-to-curved}
The Virasoro algebra can be viewed as:

\emph{Option 1 - Filtered.}
\begin{align}
F_0\text{Vir} &= \mathbb{C} \cdot \mathbf{1} \\
F_1\text{Vir} &= F_0 \oplus \mathbb{C} \cdot \partial T \\
F_2\text{Vir} &= F_1 \oplus \mathbb{C} \cdot T \\
F_3\text{Vir} &= F_2 \oplus \mathbb{C} \cdot \partial^2 T \\
&\vdots
\end{align}

\emph{Option 2 - Curved.} Generator $V = \mathbb{C} \cdot T$, curvature $\mu_0 = c \cdot \mathbf{1}$, and higher operations $m_3(T \otimes T \otimes T)$ from the Schwarzian.

The filtration $F_k$ is generated by $T$ and its derivatives up to order $k-2$. All composite
operators like $\partial^n T$ are derivatives of the single generator $T$, so the algebra is
effectively curved rather than truly filtered.

The curvature $\mu_0 = c$ captures the failure of $T$ to be a quadratic generator.
\end{example}

\begin{example}[\texorpdfstring{$W_3$}{W3}: truly filtered, not curved]\label{ex:w3-not-curved}
The $W_3$ algebra is \emph{genuinely filtered}: its generators $L$ (dimension~2) and $W$ (dimension~3) produce composite operators $(L \cdot L)$, $(L \cdot W)$, etc.\ in the OPE that are \emph{not} derivatives of $L$ or $W$.

Therefore $W_3$ cannot be reduced to a curved algebra with finite-dimensional generators. 
It requires the full filtered framework.

The distinction is that for Virasoro, $T$ and all $\partial^n T$ are ``the same'' generator (derivatives),
whereas for $W_3$, the fields $L$, $W$, and $(L \cdot L)$ are \emph{independent} generators.
This is why $W_3$ requires completion while Heisenberg and Kac--Moody do not.
\end{example}

\subsection{Explicit calculations: three examples}

\subsubsection{Heisenberg (quadratic): no completion}

\begin{example}[Heisenberg: explicit bar complex]\label{ex:heisenberg-bar-explicit}
For $\mathcal{H}_k$ with generator $J$:

\emph{Bar complex.}
\begin{align}
\bar{B}^0(\mathcal{H}_k) &= \mathbb{C} \cdot \mathbf{1} \\
\bar{B}^1(\mathcal{H}_k) &= \mathbb{C} \cdot J \\
\bar{B}^2(\mathcal{H}_k) &= \mathbb{C} \cdot (J \otimes J) \\
\bar{B}^3(\mathcal{H}_k) &= \mathbb{C} \cdot (J \otimes J \otimes J) \\
&\vdots
\end{align}

\emph{Bar differential.}

Step 1: Write the differential explicitly:
\[d: \bar{B}_1 \to \bar{B}_0\]
\[d(J(z_1) \otimes J(z_2) \otimes \eta_{12}) = \text{Res}_{z_1=z_2}[J(z_1)J(z_2) \cdot d\log(z_1-z_2)]\]

Step 2: Insert the OPE:
\begin{align}
J(z_1)J(z_2) \cdot d\log(z_1-z_2) &= \frac{k}{(z_1-z_2)^2} \cdot \frac{dz_1}{z_1-z_2} \\
&= \frac{k \, dz_1}{(z_1-z_2)^3}
\end{align}

Step 3: Compute the residue:
\[\text{Res}_{z_1=z_2}\left[\frac{k \, dz_1}{(z_1-z_2)^3}\right] = 0\]

The triple pole has zero residue, so $d = 0$ at this level.

\begin{align}
d(J) &= 0 \\
d(J \otimes J) &= 0 \quad \text{(not } k \cdot \mathbf{1}\text{; the triple pole residue vanishes)} \\
d(J \otimes J \otimes J) &= 0 \quad \text{(all pairwise OPEs have poles of order $\geq 2$, hence zero residue)}
\end{align}

\emph{Cohomology.}
\begin{align}
H^0(\bar{B}(\mathcal{H}_k)) &= \mathbb{C} \cdot \mathbf{1} \quad \text{(vacuum)} \\
H^1(\bar{B}(\mathcal{H}_k)) &\neq 0 \quad \text{(survives: the double pole means } d = 0\text{)} \\
H^n(\bar{B}(\mathcal{H}_k)) &\text{ has CE cooperad structure}
\end{align}

\emph{Koszul dual.}
\[\mathcal{H}_k^! = \mathrm{Sym}^{\mathrm{ch}}(V^*)\]
the commutative chiral algebra on the dual space $V^* = \mathrm{Hom}(V, \mathbb{C})$.

\emph{Cohomology.}
\begin{itemize}
\item $H^0 = \mathbb{C} \cdot \mathbf{1}$ (vacuum)
\item $H^1 = \bar{B}_1$ itself (since $d = 0$)
\item $H^n$ for $n \geq 2$ follow similar pattern
\end{itemize}

The full cohomology $H^*(\bar{B}(\mathcal{H}_k))$ has the structure of the CE cooperad:
\[H^*(\bar{B}(\mathcal{H}_k)) \simeq \text{CE}^!(\mathfrak{h}_k)\]

Taking the cobar dual:
\[\Omega(H^*(\bar{B}(\mathcal{H}_k))) \simeq \Omega(\text{CE}^!(\mathfrak{h}_k)) \simeq \mathcal{H}_k\]

\emph{Physical interpretation.}
\begin{itemize}
\item The Heisenberg algebra $\mathcal{H}_k$ describes a free boson
\item Its Koszul dual $\mathrm{Sym}^{\mathrm{ch}}(V^*)$ is the commutative chiral algebra on $V^*$, with curvature $m_0 = -k \cdot c$
\item Physically, this commutative dual describes the \emph{ghost system} for gauging the $U(1)$ symmetry
\item This matches the BV-BRST quantization of the gauged theory
\end{itemize}

No completion is needed: the bar complex is finite-dimensional at each degree and
converges immediately.
\end{example}

\subsubsection{Virasoro (curved): sometimes completion}

\begin{example}[Virasoro: bar complex requires completion]\label{ex:vir-bar-completion}
For $\text{Vir}_c$ with generator $T$:

\emph{Bar complex (before completion).}
\begin{align}
\bar{B}^0(\text{Vir}) &= \mathbb{C} \cdot \mathbf{1} \\
\bar{B}^1(\text{Vir}) &= \mathbb{C} \cdot T \oplus \mathbb{C} \cdot \partial T \oplus \cdots \\
\bar{B}^2(\text{Vir}) &= (\mathbb{C} \cdot T \oplus \cdots)^{\otimes 2} \\
&\vdots
\end{align}

\emph{Issue.} The space $\bar{B}^1$ is \emph{infinite-dimensional} because it includes 
all derivatives $\partial^n T$ for $n \geq 0$.

\emph{Completion.} Define the augmentation ideal:
\[I = \langle T, \partial T, \partial^2 T, \ldots \rangle\]

Complete with respect to $I$:
\[\widehat{\bar{B}}(\text{Vir}) = \varprojlim_n \bar{B}(\text{Vir})/I^n\]

\emph{Completed differential.}
\[\widehat{d}(T \otimes T) = \text{Res}(T(z)T(w)) + c \cdot \mathbf{1}\]

The curvature $c$ ensures $\widehat{d}^2 = 0$ on the completed complex.

\emph{Cohomology.}
\[H^*(\widehat{\bar{B}}(\text{Vir})) = \widehat{U(\text{Vir})}^*_{-c}\]
is the completed dual universal enveloping algebra.

Completion is essential. Without completion, the bar complex does not converge and the
Koszul dual is not well-defined.
\end{example}

\subsubsection{\texorpdfstring{$W_3$ (filtered): always completion}{W-3 (filtered): always completion}}

\begin{example}[\texorpdfstring{$W_3$}{W3}: bar complex must be completed]\label{ex:w3-bar-completion}
For $W_3$ with generators $L$ (dimension 2) and $W$ (dimension 3):

\emph{Bar complex (before completion).}
\begin{align}
\bar{B}^0(W_3) &= \mathbb{C} \cdot \mathbf{1} \\
\bar{B}^1(W_3) &= \mathbb{C} \cdot L \oplus \mathbb{C} \cdot W \oplus \text{(derivatives and composites)} \\
\bar{B}^2(W_3) &= \text{(all pairs)} \\
&\vdots
\end{align}

\emph{Problem.} Already at degree 1, we have:
\begin{itemize}
\item Generators: $L$, $W$
\item First derivatives: $\partial L$, $\partial W$
\item Second derivatives: $\partial^2 L$, $\partial^2 W$
\item Composites: $(L \cdot L)$, $(L \cdot W)$, $(W \cdot W)$
\item Higher composites: $(\partial L \cdot L)$, etc.
\end{itemize}

This is infinite-dimensional even before taking products.

\emph{Filtration.} Filter by total operator dimension:
\begin{align}
F_0 &= \mathbb{C} \cdot \mathbf{1} \\
F_2 &= F_0 \oplus \mathbb{C} \cdot L \\
F_3 &= F_2 \oplus \mathbb{C} \cdot W \oplus \mathbb{C} \cdot \partial L \\
F_4 &= F_3 \oplus \mathbb{C} \cdot \partial W \oplus \mathbb{C} \cdot \partial^2 L 
\oplus \mathbb{C} \cdot (L \cdot L) \\
&\vdots
\end{align}

\emph{Completed bar complex.}
\[\widehat{\bar{B}}(W_3) = \varprojlim_n \bar{B}(W_3)/F_n\]

\emph{Completed differential.}
\[\widehat{d}(W \otimes W) = \text{Res}(W(z)W(w)) + \text{(composite terms)} + c \cdot \mathbf{1}\]

The composite terms involve $(L \cdot L)$ and higher, which are not in the span of $\{L, W\}$.

\emph{Cohomology.}
\[H^*(\widehat{\bar{B}}(W_3)) = \widehat{\text{CoW}_3}\]
is the completed cooperad structure dual to $W_3$.

Completion is essential. Without it, the bar construction does not converge.
\end{example}

\subsection{Convergence criteria}

\begin{theorem}[Convergence of bar construction; \ClaimStatusProvedHere]\label{thm:bar-convergence}
Let $\mathcal{A}$ be a chiral algebra and write
$\bar{B}(\mathcal{A})=\bigoplus_{n\ge0}\bar{B}^n(\mathcal{A})$ with its bar-degree
filtration $F_p:=\bigoplus_{n\le p}\bar{B}^n(\mathcal{A})$.
Assume $\dim\bar{B}^n(\mathcal{A})<\infty$ for all $n$. Then the following are equivalent:
\begin{enumerate}
\item $\bar{B}(\mathcal{A})$ converges without completion, i.e. the natural map
$\bigoplus_n\bar{B}^n(\mathcal{A})\to\prod_n\bar{B}^n(\mathcal{A})$ is a
quasi-isomorphism for the bar differential.
\item \emph{Growth bound:}
$\limsup_{n\to\infty}\dim(\bar{B}^n(\mathcal{A}))^{1/n}<\infty$.
\item \emph{Filtration compatibility:}
$d(F_p)\subseteq F_p$ and $d$ lowers bar degree by one on $\gr_F\bar{B}(\mathcal{A})$.
\end{enumerate}
If (2) or (3) fails, one must use the completed bar complex
$\widehat{\bar{B}}(\mathcal{A})$.
\end{theorem}

\begin{proof}
\emph{(2)+(3) $\Rightarrow$ (1).}
Condition (3) gives a filtered complex structure on the direct sum complex and
the associated spectral sequence has
\[
E_0^{p,\bullet}=\bar{B}^p(\mathcal{A}), \qquad d_0:\bar{B}^p\to\bar{B}^{p-1}.
\]
Because each $\bar{B}^p$ is finite-dimensional and condition (2) gives uniform
at-most-exponential growth, each total degree receives only finite-dimensional
contributions, so the filtered spectral sequence is well-defined and converges
to $H^*(\bar{B}(\mathcal{A}))$. Thus no topological completion is required.
Together with Theorem~\ref{thm:conilpotency-convergence}, this means every
iterated coproduct/differential expression is finite on each element.

\emph{(1) $\Rightarrow$ (3).}
If convergence holds in the uncompleted direct sum, $d$ cannot create infinitely
many bar-degree components from a single homogeneous input; equivalently,
$d(F_p)\subseteq F_p$ and the induced differential on $\gr_F$ is degree $-1$.
Otherwise $d$ is only defined in the product completion.

\emph{(1) $\Rightarrow$ (2).}
By the Eilenberg--Moore comparison theorem \cite[Theorem~7.14]{Weibel94}, the canonical map from the direct-sum totalization to the product totalization is a quasi-isomorphism if and only if the filtration is exhaustive and complete; the growth condition~(2) ensures that the completed bar filtration is exhaustive.  Conversely, if the growth bound fails, the filtration is not exhaustive: there exist infinite-bar-degree elements in the completion that project to zero in every finite truncation, producing cohomology classes in the completion not represented by any finite bar element.  These classes obstruct the comparison quasi-isomorphism, contradicting~(1).  Hence (2) is necessary.

\emph{Quadratic finite-type case.}
For $\mathcal{A}=T(V)/(R)$ with $V$ finite-dimensional,
$\bar{B}^n(\mathcal{A})\cong (sV)^{\otimes n}$, so (2) holds with growth constant
$\dim V$, and (3) holds by definition of the bar filtration. Therefore quadratic
finite-type algebras converge without completion.
\end{proof}

\begin{remark}[Dependencies]
This proof uses:
\begin{enumerate}[label=(D\arabic*)]
\item conilpotent convergence control (Theorem~\ref{thm:conilpotency-convergence});
\item filtered-to-curved reduction inputs for non-quadratic regimes
(Theorem~\ref{thm:filtered-to-curved});
\item filtered/complete Koszul duality context (Theorem~\ref{thm:filtered-koszul-glz}).
\end{enumerate}
\end{remark}

\subsection{Physical interpretation}

Quadratic algebras correspond to free field theories (Heisenberg $\leftrightarrow$ free boson, Kac--Moody $\leftrightarrow$ WZW).  Curved algebras correspond to interacting theories with anomalies (Virasoro, with central charge $c$ measuring quantum breaking of scale invariance).  Filtered algebras correspond to theories with composite operators ($W_3$ and Toda field theory).  General algebras correspond to non-local theories ($W_\infty$), where the exact MC4 package of filtered H-level realization plus finite-stage coefficient identification remains open.

From Kontsevich's geometric viewpoint, the filtration level corresponds to the codimension of collision loci: quadratic algebras see only pairwise collisions, curved algebras see central terms from $n$-point collisions, and filtered algebras require higher-codimension strata.  The completion $\widehat{\bar{B}}(\mathcal{A})$ is the formal neighborhood of the diagonal in configuration space.

\subsection{Summary and decision tree}

\begin{remark}[Summary for practitioners]\label{rem:practitioner-takeaway}
\emph{Before computing the Koszul dual, one should determine:}
\begin{enumerate}
\item Is the algebra quadratic? $\Rightarrow$ Proceed directly
\item Is it curved with central curvature? $\Rightarrow$ Check if $\dim(\bar{B}^1) < \infty$
  \begin{itemize}
  \item If yes: No completion
  \item If no: Completion is required
  \end{itemize}
\item Does it have composite operators? $\Rightarrow$ Must complete
\item Is the generating space infinite-dimensional? $\Rightarrow$ treat as an exact MC4 frontier: first construct the filtered H-level target, then identify its finite quotients by explicit coefficient identities and finite detection
\end{enumerate}

Most vertex algebras from CFT are either quadratic or curved with finite-dimensional
$\bar{B}^1$, so Koszul duality applies.
\end{remark}

The bar complex $\bar{B}^{\mathrm{ch}}(\cA)$ is a chiral coalgebra; when the curvature is nonzero, it is a \emph{curved} coalgebra requiring Positselski's coderived categories for its homological algebra.
\fi
%%% END COMMENTED-OUT: Four-class exposition

\section{Chiral coalgebra homological algebra}
\label{sec:chiral-coalgebra-homalg}
\index{chiral coalgebra!homological algebra|textbf}
\index{Positselski!chiral lift|textbf}

The bar complex $\bar{B}^{\mathrm{ch}}(\cA)$ is a chiral coalgebra
(Theorem~\ref{thm:bar-chiral}).  At genus~$0$, it is a
DG chiral coalgebra ($\dzero^2 = 0$); at genus~$g \geq 1$ with
$\kappa(\cA) \neq 0$, it is a \emph{curved} DG chiral coalgebra
($\dfib^{\,2} = \mcurv{g} \neq 0$; Convention~\ref{conv:higher-genus-differentials}).  In the curved case, the ordinary
derived category is trivial
(Proposition~\ref{prop:curved-bar-acyclicity}), and a richer
homological algebra is needed.

The chiral analogues of Positselski's coalgebra homological
algebra~\cite{Positselski11} replace the ground field~$k$ by
$\mathcal{D}_X$ and the tensor product by $\chirtensor$; all
exactness properties are inherited from configuration space geometry.

\subsection{Chiral CDG-coalgebras}
\label{subsec:chiral-CDG-coalgebra}

\begin{definition}[Chiral CDG-coalgebra]\label{def:chiral-CDG-coalgebra}
\index{CDG-coalgebra!chiral}
A \emph{chiral CDG-coalgebra} over a smooth curve $X$ is a triple
$(C, d, h)$ where:
\begin{enumerate}
\item $C$ is a graded chiral coalgebra on $X$: a graded
  $\mathcal{D}_X$-module equipped with a comultiplication
  $\Delta\colon C \to C \chirtensor C$
  (defined via configuration space splitting maps,
  cf.\ Theorem~\ref{thm:bar-chiral}),
  a counit $\varepsilon\colon C \to \omega_X$, coassociativity,
  and the counit axioms.
\item $d\colon C \to C$ is a homogeneous endomorphism of degree~$1$
  that is an odd coderivation: the composition
  $\Delta \circ d = (d \otimes \mathrm{id} +
  \mathrm{id} \otimes d) \circ \Delta$
  holds, and $\varepsilon \circ d = 0$ on $C^{>-2}$
  (the counit annihilates $d$ except possibly in the lowest degree).
\item $h\colon C \to \omega_X$ is a homogeneous linear functional
  of degree~$2$ (the \emph{curvature}), satisfying:
  \begin{enumerate}
  \item $d^2(c) = h \ast c - c \ast h$ for all $c \in C$,
    where $h \ast c$ denotes the coaction of the curvature
    (defined via the comodule structure of $C$ over itself);
  \item $h \circ d(c) = 0$ for all $c \in C$
    (the curvature is a cocycle for the coderivation~$d$).
  \end{enumerate}
\end{enumerate}
When $h = 0$, we recover an ordinary DG chiral coalgebra.
\end{definition}

\begin{example}[The bar complex as chiral CDG-coalgebra]
\label{ex:bar-as-CDG}
\index{bar complex!as CDG-coalgebra}
For a Koszul chiral algebra $\cA$ on $X$:
\begin{itemize}
\item At genus~$0$: $\bar{B}^{(0)}(\cA) = (\bar{B}^{\mathrm{ch}}(\cA), d_B, 0)$
  is a DG chiral coalgebra ($h = 0$).
\item At genus~$g \geq 1$: $\bar{B}^{(g)}(\cA) = (\bar{B}^{\mathrm{ch}}(\cA), d_B^{(g)}, h_g)$
  is a CDG chiral coalgebra with curvature
  $h_g = m_0^{(g)} = \kappa(\cA) \cdot \lambda_g$
  (Theorem~\ref{thm:genus-universality}), where $\kappa(\cA)$ is
  the obstruction coefficient and $\lambda_g$ is the Faber--Pandharipande
  class on $\overline{\mathcal{M}}_g$.
\end{itemize}
The CDG axioms are verified as follows.  Axiom (2a): the identity
$d^2 = [m_0, -]$ is the curved $A_\infty$ relation
(Corollary~\ref{cor:critical-level-universality}).
Axiom (2b): $h \circ d = 0$ follows from $m_0$ being a scalar
(central element), so $d(m_0) = 0$.
\end{example}

\begin{remark}[Chiral CDG-coalgebra morphisms]
\label{rem:CDG-morphisms}
A morphism of chiral CDG-coalgebras $(C, d_C, h_C)$
$\to$ $(D, d_D, h_D)$ is a pair $(f, a)$ where
$f\colon C \to D$ is a morphism of graded chiral
coalgebras and $a\colon C \to \omega_X$
is a homogeneous linear function of degree~$1$ such
that
\begin{align*}
d_D(f(c)) &= f(d_C(c)) + f(a \ast c) - (-1)^{|c|}f(c \ast a), \\
h_D(f(c)) &= h_C(c) + a(d_C(c)) + a^2(c)
\end{align*}
for all $c \in C$.
Composition of morphisms is defined by
$(g, b) \circ (f, a) = (g \circ f,\allowbreak b \circ f + a)$.
This follows Positselski~\cite[\S4.1]{Positselski11}.
\end{remark}

\subsection{Chiral CDG-comodules and CDG-contramodules}
\label{subsec:chiral-CDG-comod-contra}

\begin{definition}[Chiral CDG-comodule]\label{def:chiral-CDG-comodule}
\index{CDG-comodule!chiral}
Let $(C, d, h)$ be a chiral CDG-coalgebra.  A \emph{left chiral
CDG-comodule} over $C$ is a graded left $C$-comodule $M$
(i.e., a graded $\mathcal{D}_X$-module with coaction
$\lambda\colon M \to C \chirtensor M$ satisfying coassociativity
and counit axioms) endowed with a homogeneous endomorphism
$d_M\colon M \to M$ of degree~$1$ such that:
\begin{enumerate}
\item The coaction commutes with differentials:
  $\lambda \circ d_M = (d \otimes \mathrm{id} + \mathrm{id} \otimes d_M) \circ \lambda$.
\item The curvature relation:
  $d_M^2(x) = h \ast x$ for all $x \in M$,
  where $h \ast x$ denotes the action of the curvature
  via the coaction map.
\end{enumerate}

A \emph{right chiral CDG-comodule} is defined analogously with
coaction $\rho\colon N \to N \chirtensor C$ and
$d_N^2(y) = -y \ast h$.

Morphisms of chiral CDG-comodules are homogeneous $\mathcal{D}_X$-linear
maps of degree~$0$ that are compatible with the coaction
and commute with the differential (in the usual graded sense).
\end{definition}

\begin{definition}[Chiral CDG-contramodule]\label{def:chiral-CDG-contramodule}
\index{CDG-contramodule!chiral}
Let $(C, d, h)$ be a chiral CDG-coalgebra.  A \emph{left chiral
CDG-contramodule} over $C$ is a graded left $C$-contramodule $P$
(i.e., a graded $\mathcal{D}_X$-module with contraaction
$\pi_P\colon \mathrm{Hom}^{\mathrm{ch}}(C, P) \to P$
satisfying the contraassociativity and contraunit axioms)
endowed with a
homogeneous endomorphism $d_P\colon P \to P$ of degree~$1$ such that:
\begin{enumerate}
\item The contraaction commutes with differentials on
  $\mathrm{Hom}^{\mathrm{ch}}(C, P)$ and $P$.
\item The curvature relation:
  $d_P^2(p) = h \ast p$ for all $p \in P$,
  where $h \ast p = \pi_P(h \otimes p)$ denotes the contraaction
  of the curvature.
\end{enumerate}
Morphisms of chiral CDG-contramodules are defined analogously.
\end{definition}

\begin{remark}[Contramodules in the chiral setting]
\label{rem:chiral-contramodules}
\index{contramodule!chiral}
The chiral contraaction $\pi_P\colon \mathrm{Hom}^{\mathrm{ch}}(C, P) \to P$
replaces Positselski's $\mathrm{Hom}_k(C, P) \to P$, where
$\mathrm{Hom}^{\mathrm{ch}}(C, P) := \mathrm{Hom}_{\mathcal{D}_X}(C, P)$
is the internal Hom in the chiral category.  For a conilpotent chiral
coalgebra $C$ with finite-dimensional graded pieces (as holds for
$\bar{B}^{\mathrm{ch}}(\cA)$ when $\cA$ is finitely generated over $\mathcal{D}_X$),
$\mathrm{Hom}^{\mathrm{ch}}(C, P) \cong C^* \chirtensor P$
where $C^* = \mathrm{Hom}_{\mathcal{D}_X}(C, \omega_X)$ is the
graded dual.  In this finite-type case, contramodules over $C$ are
equivalent to complete modules over the dual algebra $C^*$, recovering
the correspondence between conilpotent comodules and complete modules
already used in Theorem~\ref{thm:e1-module-koszul-duality}.
\end{remark}

\begin{remark}[No cohomology for CDG-comodules]
\label{rem:no-CDG-cohomology}
Since $d^2 \neq 0$ in a CDG-comodule (when $h \neq 0$), there is no
notion of cohomology.  This is the fundamental reason why the ordinary
derived category is inadequate at higher genus: one cannot define
acyclic objects via vanishing cohomology.  The correct
substitute is the coderived category (Definition~\ref{def:chiral-coderived}).
\end{remark}

\subsection{Chiral cotensor and cohomomorphism complexes}
\label{subsec:chiral-cotensor}

\begin{definition}[Chiral cotensor product]\label{def:chiral-cotensor}
\index{cotensor product!chiral}
Let $(C, d, h)$ be a chiral CDG-coalgebra, $N$ a right chiral
CDG-comodule, and $M$ a left chiral CDG-comodule.  The
\emph{chiral cotensor product} $N \square_C^{\mathrm{ch}} M$ is
the equalizer:
\[
N \square_C^{\mathrm{ch}} M =
\ker\bigl(\rho \chirtensor \mathrm{id} - \mathrm{id} \chirtensor \lambda\colon
N \chirtensor M \rightrightarrows N \chirtensor C \chirtensor M\bigr)
\]
in the category of graded $\mathcal{D}_X$-modules.
The differential on $N \chirtensor M$ restricts to
$N \square_C^{\mathrm{ch}} M$ (this uses the compatibility of coactions
with differentials), and the restricted differential has
$d^2 = h_N \ast (-) - (-) \ast h_M$ on the cotensor product, making
$N \square_C^{\mathrm{ch}} M$ a complex (i.e., $d^2 = 0$) precisely
when $h_N = h_M$ (the curvatures match), which holds when $N$ and $M$
are CDG-comodules over the same CDG-coalgebra~$C$.
\end{definition}

\begin{definition}[Chiral cohomomorphisms]\label{def:chiral-cohom}
\index{cohomomorphism!chiral}
For left chiral CDG-comodules $L$ and $M$ over $C$, the
\emph{chiral cohomomorphism complex} is:
\[
\mathrm{Cohom}_C^{\mathrm{ch}}(L, M) =
\{f \in \mathrm{Hom}_{\mathcal{D}_X}(L, M) :
\lambda_M \circ f = (\mathrm{id}_C \chirtensor f) \circ \lambda_L\}
\]
with differential $(d f)(x) = d_M(f(x)) - (-1)^{|f|} f(d_L(x))$.
This differential has a zero square (using the CDG-comodule axioms),
making $\mathrm{Cohom}_C^{\mathrm{ch}}(L, M)$ an honest complex.
\end{definition}

\begin{definition}[Chiral contratensor product]\label{def:chiral-contratensor}
\index{contratensor product!chiral}
For a right chiral CDG-comodule $N$ and a left chiral
CDG-contramodule $P$ over $C$, the \emph{chiral contratensor
product} $N \odot_C^{\mathrm{ch}} P$ is the coequalizer:
\[
N \odot_C^{\mathrm{ch}} P =
\mathrm{coker}\bigl(
N \chirtensor \mathrm{Hom}^{\mathrm{ch}}(C, P) \rightrightarrows N \chirtensor P
\bigr)
\]
where the two maps are
$\rho \chirtensor \pi_P$ and $\mathrm{id}_N \chirtensor \pi_P$.
The induced differential on $N \odot_C^{\mathrm{ch}} P$ has zero
square by the same curvature cancellation as for the cotensor product.
\end{definition}

\begin{lemma}[Adjunction; \ClaimStatusProvedHere]\label{lem:chiral-co-contra-adjunction}
\index{adjunction!chiral cotensor--contratensor}
There is a canonical isomorphism of complexes:
\[
\mathrm{Hom}_{\mathcal{D}_X}(N \square_C^{\mathrm{ch}} M,\, V)
\;\cong\;
\mathrm{Cohom}_C^{\mathrm{ch}}\bigl(M,\,
\mathrm{Hom}_{\mathcal{D}_X}(N, V)\bigr)
\]
for any graded $\mathcal{D}_X$-module $V$, and dually:
\[
\mathrm{Hom}_{\mathcal{D}_X}(C \chirtensor V,\, P)
\;\cong\;
\mathrm{Hom}_{\mathcal{D}_X}(V,\,
\mathrm{Hom}^{\mathrm{ch}}(C, P))
\]
establishing $\Phi_C \dashv \Psi_C$
(see Definition~\textup{\ref{def:chiral-Phi-Psi}} below).
\end{lemma}

\begin{proof}
Both isomorphisms are instances of the tensor-hom adjunction in the
chiral category.  For the first: an element of the left side is a
$\mathcal{D}_X$-linear map $f\colon N \square_C^{\mathrm{ch}} M \to V$.
By the universal property of the equalizer, this is equivalent to a
$\mathcal{D}_X$-linear map $\tilde{f}\colon N \chirtensor M \to V$
that equalizes the two coaction maps.  By the chiral tensor-hom
adjunction (which holds for holonomic $\mathcal{D}_X$-modules
by~\cite[Proposition~3.4.6]{BD04}), $\tilde{f}$ corresponds to a map
$M \to \mathrm{Hom}_{\mathcal{D}_X}(N, V)$ that is
$C$-colinear, i.e., an element of
$\mathrm{Cohom}_C^{\mathrm{ch}}(M, \mathrm{Hom}_{\mathcal{D}_X}(N, V))$.
The second isomorphism is analogous.
\end{proof}

\subsection{Coderived and contraderived categories}
\label{subsec:chiral-coderived-contraderived}

\begin{definition}[Coderived and contraderived categories]
\label{def:chiral-coderived}
\index{coderived category!chiral|textbf}
\index{contraderived category!chiral|textbf}
Let $(C, d, h)$ be a chiral CDG-coalgebra.

\emph{Exact triples.}
An exact triple of left chiral CDG-comodules is a short sequence
$0 \to L \to M \to N \to 0$ that is exact in the abelian category
of graded $C$-comodules (with closed, degree-zero morphisms).
The analogous notion applies to CDG-contramodules.

\emph{Coacyclic objects.}
A left chiral CDG-comodule $M$ is \emph{coacyclic} if it belongs to
the minimal thick subcategory of $\mathrm{Hot}(C\text{-}\mathrm{comod}^{\mathrm{ch}})$
that contains the totalizations of all exact triples and is closed
under infinite direct sums.  Denote by
$\mathrm{Acycl}^{\mathrm{co}}(C\text{-}\mathrm{comod}^{\mathrm{ch}})$
the thick subcategory of coacyclic CDG-comodules.

\emph{Contraacyclic objects.}
A left chiral CDG-contramodule $P$ is \emph{contraacyclic} if it
belongs to the minimal thick subcategory of
$\mathrm{Hot}(C\text{-}\mathrm{contra}^{\mathrm{ch}})$
that contains the totalizations of all exact triples and is closed
under infinite direct products.  Denote by
$\mathrm{Acycl}^{\mathrm{ctr}}(C\text{-}\mathrm{contra}^{\mathrm{ch}})$
the thick subcategory of contraacyclic CDG-contramodules.

\emph{The exotic derived categories.}
\begin{align}
D^{\mathrm{co}}(C\text{-}\mathrm{comod}^{\mathrm{ch}})
&:= \mathrm{Hot}(C\text{-}\mathrm{comod}^{\mathrm{ch}})
\,/\, \mathrm{Acycl}^{\mathrm{co}}(C\text{-}\mathrm{comod}^{\mathrm{ch}})
\label{eq:chiral-coderived}\\
D^{\mathrm{ctr}}(C\text{-}\mathrm{contra}^{\mathrm{ch}})
&:= \mathrm{Hot}(C\text{-}\mathrm{contra}^{\mathrm{ch}})
\,/\, \mathrm{Acycl}^{\mathrm{ctr}}(C\text{-}\mathrm{contra}^{\mathrm{ch}})
\label{eq:chiral-contraderived}
\end{align}
\end{definition}

\begin{remark}[Comparison with ordinary derived category]
\label{rem:exotic-vs-ordinary}
When $h = 0$ (genus~$0$), CDG-comodules are ordinary DG-comodules
and one can also form the standard derived category
$D(C\text{-}\mathrm{comod}^{\mathrm{ch}})$
by localizing at acyclic objects (those with $H^*(M) = 0$).  In general,
$\mathrm{Acycl}^{\mathrm{co}} \supset \mathrm{Acycl}$,
so $D^{\mathrm{co}}$ is a quotient of $D$.  When $C$ has
finite homological dimension (e.g., when $\cA$ is Koszul with finite
global dimension), the two categories coincide
(Positselski~\cite[\S4.5]{Positselski11}).  When $h \neq 0$, the standard
derived category is trivial (no cohomology exists), while
$D^{\mathrm{co}}$ retains rich structure.
\end{remark}

\subsection{Injective comodules and projective contramodules}
\label{subsec:chiral-inj-proj}

\begin{definition}[Cofree chiral CDG-comodule]
\label{def:cofree-chiral-comod}
\index{cofree comodule!chiral}
For a graded $\mathcal{D}_X$-module $V$, the \emph{cofree graded
chiral $C$-comodule} on $V$ is:
\[
J(V) := C \chirtensor V
\]
with coaction $\Delta \chirtensor \mathrm{id}_V\colon
C \chirtensor V \to C \chirtensor C \chirtensor V$.
The CDG-comodule differential is
$d_{J(V)}(c \otimes v) = d(c) \otimes v$,
and the curvature relation $d_{J(V)}^2 = h \ast (-)$ is inherited
from~$C$.
\end{definition}

\begin{proposition}[Injective and projective resolutions;
\ClaimStatusProvedHere]\label{prop:chiral-inj-proj-resolutions}
\index{injective resolution!chiral CDG-comodule}
\index{projective resolution!chiral CDG-contramodule}
Let $(C, d, h)$ be a conilpotent chiral CDG-coalgebra with
finite-dimensional graded pieces.
\begin{enumerate}[label=\textup{(\alph*)}]
\item For any left chiral CDG-comodule $M$, the cofree chiral
  comodule $J(M) = C \chirtensor M$ is \emph{injective} in the
  abelian category of graded $C^{\#}$-comodules (where $C^{\#}$
  denotes $C$ with forgotten differential and curvature).
\item For any left chiral CDG-contramodule $P$, the free chiral
  contramodule $F(P) = \mathrm{Hom}^{\mathrm{ch}}(C, P)$ is
  \emph{projective} in the abelian category of graded
  $C^{\#}$-contramodules.
\item The homotopy categories admit semiorthogonal decompositions:
  the coderived category $D^{\mathrm{co}}(C\text{-}\mathrm{comod}^{\mathrm{ch}})$
  is equivalent to the homotopy category of CDG-comodules
  with injective underlying graded comodules, and
  $D^{\mathrm{ctr}}(C\text{-}\mathrm{contra}^{\mathrm{ch}})$
  is equivalent to the homotopy category of CDG-contramodules
  with projective underlying graded contramodules.
\end{enumerate}
\end{proposition}

\begin{proof}
\emph{Part (a).}
Let $0 \to L \to M \to N \to 0$ be an exact sequence of graded
$C^{\#}$-comodules.  We must show that
$0 \to \mathrm{Hom}_{C^{\#}}(N, J(V)) \to \mathrm{Hom}_{C^{\#}}(M, J(V))
\to \mathrm{Hom}_{C^{\#}}(L, J(V)) \to 0$
is exact.  By the tensor-hom adjunction in the chiral category:
$\mathrm{Hom}_{C^{\#}}(M, C \chirtensor V)
\cong \mathrm{Hom}_{\mathcal{D}_X}(M, V)$,
and the functor $\mathrm{Hom}_{\mathcal{D}_X}(-, V)$ is exact
on holonomic $\mathcal{D}_X$-modules (since holonomic modules have
finite length).

\emph{Part (b).}
Dual to (a): for an exact sequence
$0 \to P \to Q \to R \to 0$ of graded $C^{\#}$-contramodules,
$\mathrm{Hom}_{C^{\#}}(\mathrm{Hom}^{\mathrm{ch}}(C, V), -)$
is exact because
$\mathrm{Hom}_{C^{\#}}(\mathrm{Hom}^{\mathrm{ch}}(C, V), P)
\cong \mathrm{Hom}_{\mathcal{D}_X}(V, P)$.

\emph{Part (c).}
For any CDG-comodule $M$, the cobar resolution provides a
functorial injective resolution: form
$J = \bigoplus_{n=0}^{\infty} C^{\chirtensor (n+1)} \chirtensor M$
with the standard bar-type differential (the chiral analogue of
Positselski~\cite[\S4.4, proof of Theorem]{Positselski11}).
The closed morphism $M \to J$ has the property that
$\mathrm{cone}(M \to J)$ is coacyclic (each quotient
$\tau_{\leq n}J / \tau_{\leq n-1}J$ is a cofree CDG-comodule, and
the cone is built from these by exact triangles and countable direct
sums).  The projectivity statement for contramodules is dual:
take the bar resolution
$\cdots \to \mathrm{Hom}^{\mathrm{ch}}(C^{\chirtensor 2}, P)
\to \mathrm{Hom}^{\mathrm{ch}}(C, P) \to P$
and observe that the cone is contraacyclic (built from free
contramodules by exact triangles and countable direct products).

The semiorthogonal decomposition follows formally: the localization
functor from the full homotopy category to $D^{\mathrm{co}}$
restricts to an equivalence on the full subcategory of objects with
injective underlying graded comodule (since coacyclic objects with
injective underlying comodule are contractible, by the same argument as
Positselski~\cite[\S4.4]{Positselski11}, using the injective
resolution of the previous paragraph).  The dual statement holds for
$D^{\mathrm{ctr}}$.
\end{proof}

\begin{proposition}[Explicit CDG Hom-complex; \ClaimStatusProvedHere]
\label{prop:cdg-hom-complex}
\index{CDG-comodule!Hom-complex|textbf}
Let $(C, d_C, h)$ be a chiral CDG-coalgebra and let $M$, $N$ be
left chiral CDG-comodules over~$C$.  The \emph{CDG Hom-complex}
$\underline{\mathrm{Hom}}_C^{\mathrm{ch}}(M, N)$ is the graded
$\mathcal{D}_X$-module of graded $C^{\#}$-comodule morphisms,
with differential
\begin{equation}\label{eq:cdg-hom-differential}
d_{\mathrm{Hom}}(f) \;=\; d_N \circ f
\;-\; (-1)^{|f|}\, f \circ d_M.
\end{equation}
This differential satisfies $d_{\mathrm{Hom}}^2(f) = [h_N, f] - [h_M, f]$
where $h_M$, $h_N$ denote the curvature endomorphisms
$h \ast (-)$ on $M$ and $N$ respectively.  In particular:
\begin{enumerate}[label=\textup{(\alph*)}]
\item When $h = 0$ \textup{(}genus~$0$\textup{)},
  $d_{\mathrm{Hom}}^2 = 0$ and the Hom-complex is a genuine
  DG-module.
\item When $h \neq 0$, the Hom-complex is a \emph{CDG-module}
  with curvature $h_{\mathrm{Hom}}(f) = h_N \circ f - f \circ h_M$.
  For endomorphisms ($M = N$),
  $d_{\mathrm{Hom}}^2(f) = [h_M, f]$, so $d_{\mathrm{Hom}}$ is
  a genuine differential on the \emph{center}
  $Z(\mathrm{End}_C(M)) = \{f : h_M \circ f = f \circ h_M\}$.
\end{enumerate}
\end{proposition}

\begin{proof}
Direct computation.  For $f \in \underline{\mathrm{Hom}}_C^{\mathrm{ch}}(M, N)^k$:
\begin{align*}
d_{\mathrm{Hom}}^2(f)
&= d_N \circ \bigl(d_N \circ f - (-1)^k f \circ d_M\bigr)
  - (-1)^{k+1}\bigl(d_N \circ f - (-1)^k f \circ d_M\bigr) \circ d_M \\
&= d_N^2 \circ f + (-1)^{k+1}\, d_N \circ f \circ d_M
  + (-1)^{k+1}\, d_N \circ f \circ d_M + f \circ d_M^2 \\
&= d_N^2 \circ f - f \circ d_M^2 \\
&= (h_N \ast -) \circ f - f \circ (h_M \ast -),
\end{align*}
where the last step uses the CDG relation $d^2 = h \ast (-)$ on
$M$ and~$N$.  When $M = N$, this is $[h_M, f]$, which vanishes
on central endomorphisms.
\end{proof}

\begin{corollary}[Contractibility of coacyclic injectives; \ClaimStatusProvedHere]
\label{cor:coacyclic-injective-contractible}
\index{coacyclic!contractibility criterion|textbf}
Let $(C, d, h)$ be a conilpotent chiral CDG-coalgebra with
finite-dimensional graded pieces, and let $M$ be a chiral
CDG-comodule with injective underlying graded $C^{\#}$-comodule.
Then $M$ is coacyclic if and only if it admits a
\emph{contracting homotopy}: a degree~$-1$ graded
$C^{\#}$-comodule endomorphism $s \colon M \to M$ satisfying
\begin{equation}\label{eq:contracting-homotopy-cdg}
d_M \circ s + s \circ d_M \;=\; \mathrm{id}_M.
\end{equation}
\end{corollary}

\begin{proof}
If such an $s$ exists, then $\mathrm{id}_M = d_{\mathrm{Hom}}(s)$
in the CDG Hom-complex of
Proposition~\ref{prop:cdg-hom-complex} (with $M = N$), so $M$ is
null-homotopic and \emph{a fortiori} coacyclic.

Conversely, suppose $M$ is coacyclic with injective underlying
graded comodule.  By the semiorthogonal decomposition in
Proposition~\ref{prop:chiral-inj-proj-resolutions}(c),
$D^{\mathrm{co}}(C\text{-}\mathrm{comod}^{\mathrm{ch}})$
is equivalent to
$\mathrm{Hot}(C\text{-}\mathrm{comod}^{\mathrm{ch}}_{\mathrm{inj}})$.
A coacyclic object that already has injective underlying comodule
represents the zero object in this homotopy category, hence is
null-homotopic: there exists a degree~$-1$ closed morphism
$s$ with $d_{\mathrm{Hom}}(s) = \mathrm{id}_M$.
Expanding via~\eqref{eq:cdg-hom-differential} gives~\eqref{eq:contracting-homotopy-cdg}.
\end{proof}

\subsection{The correspondence functors}
\label{subsec:chiral-correspondence-functors}

\begin{definition}[Functors \texorpdfstring{$\Phi_C^{\mathrm{ch}}$}{Phi_C^ch} and \texorpdfstring{$\Psi_C^{\mathrm{ch}}$}{Psi_C^ch}]
\label{def:chiral-Phi-Psi}
\index{Positselski!functors PhiPsi@$\Phi_C$, $\Psi_C$}
Let $(C, d, h)$ be a chiral CDG-coalgebra.
\begin{itemize}
\item For a left chiral CDG-contramodule $P$, define
  $\Phi_C^{\mathrm{ch}}(P)$ to be the left chiral CDG-comodule
  whose underlying graded $\mathcal{D}_X$-module is the
  chiral contratensor product $C \odot_C^{\mathrm{ch}} P$.
  Concretely, $\Phi_C^{\mathrm{ch}}(P)$ is a quotient of
  $C \chirtensor P$; the comodule structure comes from the
  comultiplication on the left factor~$C$, and the differential is
  induced by the differentials on $C$ and $P$ via the standard
  formula for the tensor product of graded $\mathcal{D}_X$-modules
  with differentials.
\item For a left chiral CDG-comodule $M$, define
  $\Psi_C^{\mathrm{ch}}(M)$ to be the left chiral CDG-contramodule
  whose underlying graded $\mathcal{D}_X$-module is
  $\mathrm{Hom}_C^{\mathrm{ch}}(C, M) = \mathrm{Cohom}_C^{\mathrm{ch}}(C, M)$.
  The contramodule structure comes from the comultiplication
  on $C$, and the differential is induced from $d_C$ and $d_M$.
\end{itemize}
These define DG-functors:
\begin{align*}
\Phi_C^{\mathrm{ch}}\colon \mathrm{DG}(C\text{-}\mathrm{contra}^{\mathrm{ch}})
&\longrightarrow \mathrm{DG}(C\text{-}\mathrm{comod}^{\mathrm{ch}}), \\
\Psi_C^{\mathrm{ch}}\colon \mathrm{DG}(C\text{-}\mathrm{comod}^{\mathrm{ch}})
&\longrightarrow \mathrm{DG}(C\text{-}\mathrm{contra}^{\mathrm{ch}}).
\end{align*}
\end{definition}

\begin{lemma}[Key properties of \texorpdfstring{$\Phi_C^{\mathrm{ch}}$}{Phi_C^ch} and
\texorpdfstring{$\Psi_C^{\mathrm{ch}}$}{Psi_C^ch}; \ClaimStatusProvedHere]
\label{lem:Phi-Psi-properties}
\begin{enumerate}[label=\textup{(\alph*)}]
\item $\Phi_C^{\mathrm{ch}}$ is left adjoint to $\Psi_C^{\mathrm{ch}}$
  on the homotopy categories.
\item $\Phi_C^{\mathrm{ch}}$ maps the free graded contramodule
  $\mathrm{Hom}^{\mathrm{ch}}(C, V)$ to the cofree graded comodule
  $C \chirtensor V$, for any graded $\mathcal{D}_X$-module $V$.
\item $\Psi_C^{\mathrm{ch}}$ maps the cofree graded comodule
  $C \chirtensor V$ to the free graded contramodule
  $\mathrm{Hom}^{\mathrm{ch}}(C, V)$.
\item $\Phi_C^{\mathrm{ch}}$ maps projective graded contramodules
  to injective graded comodules, and $\Psi_C^{\mathrm{ch}}$ maps
  injective graded comodules to projective graded contramodules.
\end{enumerate}
\end{lemma}

\begin{proof}
\emph{Part (a).}
The adjunction $\Phi_C^{\mathrm{ch}} \dashv \Psi_C^{\mathrm{ch}}$
follows from the standard isomorphism
$\mathrm{Hom}_{\mathcal{D}_X}(C \chirtensor V, P)
\cong \mathrm{Hom}_{\mathcal{D}_X}(V, \mathrm{Hom}^{\mathrm{ch}}(C, P))$
(the chiral tensor-hom adjunction), which makes
$\Phi_C^{\mathrm{ch}}$ left adjoint to $\Psi_C^{\mathrm{ch}}$ as
DG-functors (Lemma~\ref{lem:chiral-co-contra-adjunction}).

\emph{Parts (b) and (c).}
The free graded contramodule on $V$ is
$\mathrm{Hom}^{\mathrm{ch}}(C, V) = \mathrm{Hom}_{\mathcal{D}_X}(C, V)$.
Then:
\[
\Phi_C^{\mathrm{ch}}(\mathrm{Hom}^{\mathrm{ch}}(C, V))
= C \odot_C^{\mathrm{ch}} \mathrm{Hom}^{\mathrm{ch}}(C, V).
\]
By the contramodule-comodule correspondence at the graded level
(cf.\ the example in
Positselski~\cite[\S5.1]{Positselski11}), the
contratensor product of $C$ with the free contramodule on $V$ is
canonically isomorphic to the cofree comodule $C \chirtensor V$.
In the chiral setting, this isomorphism follows from the
tensor-hom adjunction for $\mathcal{D}_X$-modules:
\begin{align*}
C \odot_C^{\mathrm{ch}} \mathrm{Hom}^{\mathrm{ch}}(C, V)
&\cong \mathrm{coker}\bigl(
C \chirtensor \mathrm{Hom}^{\mathrm{ch}}(C, \mathrm{Hom}^{\mathrm{ch}}(C, V))
\rightrightarrows C \chirtensor \mathrm{Hom}^{\mathrm{ch}}(C, V)
\bigr) \\
&\cong C \chirtensor V,
\end{align*}
where the last step uses the counit of the adjunction
$\mathrm{ev}\colon \mathrm{Hom}^{\mathrm{ch}}(C, V) \chirtensor C
\to V$ and the coassociativity of $C$.  Part~(c) is the dual computation.

\emph{Part (d).}
Combine (b)--(c) with
Proposition~\ref{prop:chiral-inj-proj-resolutions}(a)--(b):
free graded contramodules are projective and cofree graded comodules
are injective, so $\Phi_C^{\mathrm{ch}}$ sends projective objects
to injective objects and vice versa.
\end{proof}

\subsection{The chiral comodule-contramodule correspondence}
\label{subsec:chiral-co-contra-correspondence}

\begin{theorem}[Chiral comodule-contramodule correspondence;
\ClaimStatusProvedHere]
\label{thm:chiral-co-contra-correspondence}
\index{comodule-contramodule correspondence!chiral|textbf}
\index{Positselski!chiral correspondence|textbf}
Let $(C, d, h)$ be a conilpotent chiral CDG-coalgebra on a smooth
curve $X$ with finite-dimensional graded pieces.  The derived functors
\begin{align*}
\mathbb{L}\Phi_C^{\mathrm{ch}}\colon
D^{\mathrm{ctr}}(C\text{-}\mathrm{contra}^{\mathrm{ch}})
&\longrightarrow
D^{\mathrm{co}}(C\text{-}\mathrm{comod}^{\mathrm{ch}}), \\
\mathbb{R}\Psi_C^{\mathrm{ch}}\colon
D^{\mathrm{co}}(C\text{-}\mathrm{comod}^{\mathrm{ch}})
&\longrightarrow
D^{\mathrm{ctr}}(C\text{-}\mathrm{contra}^{\mathrm{ch}})
\end{align*}
are mutually inverse equivalences of triangulated categories.
\end{theorem}

\begin{proof}
The proof follows Positselski~\cite[\S5.2]{Positselski11}, with the
ordinary tensor product replaced by the chiral tensor product
$\chirtensor$ and exactness properties established via the geometry
of $\mathcal{D}_X$-modules on configuration spaces.  We verify
each step.

\emph{Step~1: Derived functors.}
By Proposition~\ref{prop:chiral-inj-proj-resolutions}(c),
the contraderived and coderived categories
\begin{align*}
D^{\mathrm{ctr}}(C\text{-}\mathrm{contra}^{\mathrm{ch}})
&\simeq K_{\mathrm{proj}}(C\text{-}\mathrm{contra}^{\mathrm{ch}}),\\
D^{\mathrm{co}}(C\text{-}\mathrm{comod}^{\mathrm{ch}})
&\simeq K_{\mathrm{inj}}(C\text{-}\mathrm{comod}^{\mathrm{ch}})
\end{align*}
are equivalent to the homotopy categories of
CDG-contra\-modules (resp.\ CDG-comodules) with
projective (resp.\ injective) underlying graded module.
The left derived functor~$\mathbb{L}\Phi_C^{\mathrm{ch}}$
restricts to projective contramodules;
$\mathbb{R}\Psi_C^{\mathrm{ch}}$ restricts to injective comodules.

\emph{Step~2: Mutual inverse on generators.}
By Lemma~\ref{lem:Phi-Psi-properties}(b)--(c), $\Phi_C^{\mathrm{ch}}$
sends the free graded contramodule $\mathrm{Hom}^{\mathrm{ch}}(C, V)$
to the cofree graded comodule $C \chirtensor V$, and
$\Psi_C^{\mathrm{ch}}$ sends $C \chirtensor V$ back to
$\mathrm{Hom}^{\mathrm{ch}}(C, V)$.  These are the generating objects
for the respective categories (any CDG-comodule has an injective
resolution by cofree comodules, and any CDG-contramodule has a
projective resolution by free contramodules, by
Proposition~\ref{prop:chiral-inj-proj-resolutions}).

\emph{Step~3: Equivalence on full triangulated subcategories.}
We claim that the restrictions of $\Phi_C^{\mathrm{ch}}$ and
$\Psi_C^{\mathrm{ch}}$ to the full triangulated subcategories
\begin{align*}
\mathrm{Hot}(C\text{-}\mathrm{contra}^{\mathrm{ch}}_{\mathrm{proj}})
&\subset \mathrm{Hot}(C\text{-}\mathrm{contra}^{\mathrm{ch}}), \\
\mathrm{Hot}(C\text{-}\mathrm{comod}^{\mathrm{ch}}_{\mathrm{inj}})
&\subset \mathrm{Hot}(C\text{-}\mathrm{comod}^{\mathrm{ch}})
\end{align*}
are mutually inverse equivalences.

To see this, observe that the unit and counit natural transformations
\[
\eta\colon \mathrm{id} \to \Psi_C^{\mathrm{ch}} \circ \Phi_C^{\mathrm{ch}},
\qquad
\varepsilon\colon \Phi_C^{\mathrm{ch}} \circ \Psi_C^{\mathrm{ch}} \to \mathrm{id}
\]
are isomorphisms on free contramodules and cofree comodules
(Step~2).  Since these objects generate the respective
homotopy categories (every object is built from generators by
shifts, cones, and countable (co)products),
and both $\Phi_C^{\mathrm{ch}}$ and $\Psi_C^{\mathrm{ch}}$ preserve
exact triangles and countable (co)products, the natural
transformations $\eta$ and $\varepsilon$ are isomorphisms
on all objects with projective (resp.\ injective) underlying graded
structure.

\emph{Step~4: Descent to exotic derived categories.}
To pass from the full homotopy categories to $D^{\mathrm{co}}$ and
$D^{\mathrm{ctr}}$, we verify that $\Phi_C^{\mathrm{ch}}$ maps
contraacyclic CDG-contramodules to coacyclic CDG-comodules, and
$\Psi_C^{\mathrm{ch}}$ maps coacyclic CDG-comodules to
contraacyclic CDG-contramodules.

For $\Phi_C^{\mathrm{ch}}$: since $\Phi_C^{\mathrm{ch}}$ is a
left adjoint, it preserves (all) colimits, in particular coproducts
and cokernels.  A contraacyclic CDG-contramodule is built from
totalizations of exact triples and direct products.  Now,
$\Phi_C^{\mathrm{ch}}$ preserves exact triples (being a left adjoint
of an exact functor, hence right exact; and by
Lemma~\ref{lem:Phi-Psi-properties}(d) it sends projective
contramodules to injective comodules, so the left derived functor
is exact).  The image of a totalization under $\Phi_C^{\mathrm{ch}}$
is a totalization, and the image of a direct product is computed
using the cofree resolution from Step~2.  Thus
$\Phi_C^{\mathrm{ch}}$ preserves contraacyclic $\to$ coacyclic.
The argument for $\Psi_C^{\mathrm{ch}}$ is dual.

\emph{Step~5: Conclusion.}
Combining Steps~3 and~4:  $\mathbb{L}\Phi_C^{\mathrm{ch}}$ and
$\mathbb{R}\Psi_C^{\mathrm{ch}}$ are well-defined triangulated
functors between $D^{\mathrm{ctr}}$ and $D^{\mathrm{co}}$, they
are mutually inverse on the generating subcategories (projective
contramodules $\leftrightarrow$ injective comodules), and both
categories are compactly generated by finite-dimensional objects
(using conilpotency and finite-type grading; the argument parallels
Positselski~\cite[\S5.5]{Positselski11}, with the key input that any
graded $C$-comodule is the union of its finite-dimensional
subcomodules, which holds for conilpotent chiral coalgebras because
the conformal weight grading bounds the coaction filtration).
By the uniqueness of extensions of equivalences from compact generators
to the full compactly generated category
(cf.~\cite[\S5.5]{Positselski11}), the equivalence extends to all objects.
\end{proof}

\begin{remark}[Hypotheses]\label{rem:co-contra-hypotheses}
The two key hypotheses---conilpotency and finite-type grading---are
satisfied by $C = \bar{B}^{\mathrm{ch}}(\cA)$ whenever $\cA$ is a
finitely generated chiral algebra with finite-dimensional conformal
weight spaces (which includes all Koszul chiral algebras arising in
this monograph: Kac--Moody, Virasoro, $W$-algebras, Heisenberg, free
fields, and Yangians).  Conilpotency was established in
Theorem~\ref{thm:coalgebra-via-NAP}(4); finite-type grading follows
from the finite-generation hypothesis on~$\cA$.
\end{remark}

\subsection{Application: the Positselski equivalence for chiral algebras}
\label{subsec:positselski-chiral-equivalence}

The chiral comodule-contramodule correspondence yields the derived module category equivalence at all genera.

\begin{theorem}[Positselski equivalence for chiral algebras;
\ClaimStatusProvedHere]
\label{thm:positselski-chiral-proved}
\index{Positselski!chiral equivalence|textbf}
\index{comodule-contramodule correspondence!chiral Koszul|textbf}
For a Koszul chiral algebra $\cA$ on a smooth curve $X$ with
curved bar complex $C = \bar{B}^{\mathrm{ch}}(\cA)$
(a conilpotent chiral CDG-coalgebra by
Example~\textup{\ref{ex:bar-as-CDG}}), there is an equivalence of
triangulated categories:
\begin{equation}\label{eq:positselski-chiral-proved}
D^{\mathrm{co}}(\cA\text{-}\mathrm{CoMod}^{\mathrm{conil,\,ch}})
\;\simeq\;
D^{\mathrm{ctr}}(\cA^!\text{-}\mathrm{ContraMod}^{\mathrm{ch}})
\end{equation}
between the coderived category of conilpotent chiral
$\cA$-comodules and the contraderived category of chiral
$\cA^!$-contramodules.

At genus~$0$ (where $h = 0$), this reduces to the module Koszul
duality of
Theorem~\textup{\ref{thm:e1-module-koszul-duality}}.
At genus~$g \geq 1$ (where $h = m_0^{(g)} \neq 0$), the ordinary
derived categories are trivial, and the coderived/contraderived
categories provide the correct framework.
\end{theorem}

\begin{proof}
Apply Theorem~\ref{thm:chiral-co-contra-correspondence} with
$C = \bar{B}^{\mathrm{ch}}(\cA)$.

\emph{Identification of comodule category.}
A conilpotent chiral CDG-comodule over
$C = \bar{B}^{\mathrm{ch}}(\cA)$ is a graded $\mathcal{D}_X$-module~$M$
with coaction $M \to \bar{B}^{\mathrm{ch}}(\cA) \chirtensor M$ and
differential satisfying $\dfib^{\,2} = \mcurv{g} \ast (-)$ (Convention~\ref{conv:higher-genus-differentials}).  This is
precisely a (curved) $\cA$-module in the sense that the coaction
encodes the $\cA$-module structure via the bar construction:
$\cA\text{-}\mathrm{CoMod}^{\mathrm{conil,\,ch}}
\cong \bar{B}^{\mathrm{ch}}(\cA)\text{-}\mathrm{comod}^{\mathrm{ch}}$
(this is the module-level bar construction,
cf.\ the proof of Theorem~\ref{thm:e1-module-koszul-duality},
Step~1).

\emph{Identification of contramodule category.}
The dual algebra $C^* = \bar{B}^{\mathrm{ch}}(\cA)^*$ is canonically
identified with $\cA^!$ (the Koszul dual chiral algebra, via
Theorem~\ref{thm:bar-computes-dual}).  A chiral CDG-contramodule
over $C$ is a graded $\mathcal{D}_X$-module $P$ with contraaction
$\mathrm{Hom}^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\cA), P) \to P$,
which (by the finite-type duality of Remark~\ref{rem:chiral-contramodules})
is equivalent to a complete (pro-nilpotent) module over~$\cA^!$:
$\cA^!\text{-}\mathrm{ContraMod}^{\mathrm{ch}}
\cong \bar{B}^{\mathrm{ch}}(\cA)\text{-}\mathrm{contra}^{\mathrm{ch}}$.

\emph{Conclusion.}
The hypotheses of Theorem~\ref{thm:chiral-co-contra-correspondence}
are satisfied: $\bar{B}^{\mathrm{ch}}(\cA)$ is conilpotent
(Theorem~\ref{thm:coalgebra-via-NAP}(4)) with finite-dimensional
graded pieces (since $\cA$ is finitely generated with
finite-dimensional conformal weight spaces).  The equivalence
$D^{\mathrm{co}}(C\text{-}\mathrm{comod}^{\mathrm{ch}})
\simeq D^{\mathrm{ctr}}(C\text{-}\mathrm{contra}^{\mathrm{ch}})$
of Theorem~\ref{thm:chiral-co-contra-correspondence} therefore yields
\eqref{eq:positselski-chiral-proved}.
\end{proof}

\begin{theorem}[Full derived module equivalence; \ClaimStatusProvedHere]
\label{thm:full-derived-module-equiv-proved}
\index{derived category!full module equivalence|textbf}
\index{Positselski!full derived equivalence|textbf}
For a Koszul chiral algebra $\cA$ with curved bar complex
$\bar{B}(\cA)$, there is a triangulated equivalence:
\begin{equation}\label{eq:full-derived-equiv-proved}
D^b(\mathrm{Mod}^{\mathrm{compl}}(\cA))
\;\simeq\;
D^{\mathrm{co}}(\mathrm{CoMod}^{\mathrm{conil}}(\cA^!))
\end{equation}
where $\mathrm{Mod}^{\mathrm{compl}}(\cA)$ denotes the category
of complete \textup{(}pro-nilpotent\textup{)} $\cA$-modules
and $\mathrm{CoMod}^{\mathrm{conil}}(\cA^!)$ denotes the
category of conilpotent $\cA^!$-comodules.

This equivalence induces the Ext duality:
\begin{equation}\label{eq:ext-duality-proved}
\mathrm{Ext}^n_{\cA}(M_1, M_2)
\;\cong\;
\mathrm{Ext}^{d-n}_{\cA^!}(\Phi(M_1), \Phi(M_2))^{\vee}
\end{equation}
where $d$ is the global dimension of $\cA$ and
$\Phi = \bar{B}_{\cA}$ is the bar functor.
\end{theorem}

\begin{proof}
\emph{Step~1.}
By Theorem~\ref{thm:positselski-chiral-proved}:
\[
D^{\mathrm{co}}(\cA\text{-}\mathrm{CoMod}^{\mathrm{conil,\,ch}})
\simeq
D^{\mathrm{ctr}}(\cA^!\text{-}\mathrm{ContraMod}^{\mathrm{ch}}).
\]

\emph{Step~2.}
By Remark~\ref{rem:chiral-contramodules}, complete $\cA^!$-modules
are equivalent to chiral CDG-contramodules over $\bar{B}^{\mathrm{ch}}(\cA)$.
Moreover, the contraderived category of such contramodules is
identified with the bounded derived category of complete
$\cA$-modules:
$D^{\mathrm{ctr}}(\cA^!\text{-}\mathrm{ContraMod}^{\mathrm{ch}})
\simeq D^b(\mathrm{Mod}^{\mathrm{compl}}(\cA))$.
This identification uses the finite homological dimension:
since $\cA$ is Koszul, the bar complex
$\bar{B}^{\mathrm{ch}}(\cA)$ has finite homological dimension
(bounded by the global dimension of the underlying operadic
structure), so the contraderived and ordinary derived categories
coincide on the algebra side
(Positselski~\cite[\S4.5]{Positselski11}).

\emph{Step~3.}
Combining: $D^b(\mathrm{Mod}^{\mathrm{compl}}(\cA)) \simeq
D^{\mathrm{co}}(\mathrm{CoMod}^{\mathrm{conil}}(\cA^!))$.

\emph{Ext duality.}
The equivalence $\Phi = \bar{B}_{\cA}$ sends
$\mathrm{Hom}^*_{\cA}(M_1, M_2)$ to
$\mathrm{Cohom}^*_{\cA^!}(\Phi(M_1), \Phi(M_2))$.
By the comodule-contramodule correspondence
(Theorem~\ref{thm:chiral-co-contra-correspondence}, \S5.3 of
\cite{Positselski11}), the cohomomorphism complex is identified
with the Ext complex on the dual side, with the dimension shift
coming from Verdier duality on configuration spaces:
$\mathrm{Ext}^n_{\cA}(M_1, M_2) \cong
\mathrm{Ext}^{d-n}_{\cA^!}(\Phi(M_1), \Phi(M_2))^{\vee}$.
\end{proof}

\begin{remark}[Relation to genus-0 module Koszul duality]
\label{rem:genus-0-recovery}
At genus~$0$, the curvature $h = 0$, so CDG-comodules reduce to
DG-comodules, the coderived category reduces to the ordinary derived
category, and Theorem~\ref{thm:full-derived-module-equiv-proved}
recovers the module Koszul duality of
Theorem~\ref{thm:e1-module-koszul-duality}:
\[
D^b(\mathrm{Mod}^{\mathrm{compl}}(\cA))
\simeq D(\mathrm{CoMod}^{\mathrm{conil}}(\cA^!)).
\]
The virtue of the coderived/contraderived framework is that it
provides the correct generalization to genus~$g \geq 1$, where the
curvature $m_0^{(g)} \neq 0$ makes the ordinary derived category
trivial.
\end{remark}

\begin{remark}[The role of the configuration space geometry]
\label{rem:config-space-role}
The proof of the chiral comodule-contramodule correspondence
(Theorem~\ref{thm:chiral-co-contra-correspondence}) uses the
geometry of configuration spaces in three places:
\begin{enumerate}
\item \emph{Exactness of the chiral tensor product.}
  The tensor-hom adjunction for holonomic $\mathcal{D}_X$-modules
  on $\overline{C}_n(X)$ ensures that cofree comodules are injective
  and free contramodules are projective
  (Proposition~\ref{prop:chiral-inj-proj-resolutions}).
\item \emph{Conilpotency from conformal weight.}
  The conformal weight grading on $\bar{B}^{\mathrm{ch}}(\cA)$
  (inherited from $\cA$) ensures conilpotency
  (Theorem~\ref{thm:coalgebra-via-NAP}(4)), which is needed for
  the compact generation argument in Step~5 of the proof.
\item \emph{Finite-dimensionality from holonomicity.}
  The holonomicity of the bar complex on each configuration space
  stratum (Lemma~\ref{lem:bar-holonomicity}) ensures
  finite-dimensional graded pieces, which is
  needed for the duality between contramodules and complete modules
  (Remark~\ref{rem:chiral-contramodules}).
\end{enumerate}
These geometric inputs are specific to the chiral setting and have
no analogue in Positselski's ground-field framework.
\end{remark}

%================================================================
% SECTION: BAR-COBAR INVERSION - COMPLETE QUASI-ISOMORPHISM
%================================================================

\section{Bar-cobar inversion}
\label{sec:bar-cobar-inversion-quasi-iso}

\subsection{Statement of the main result}

\begin{theorem}[Bar-cobar inversion is quasi-isomorphism; \ClaimStatusProvedHere]\label{thm:bar-cobar-inversion-qi}
\textup{[Regime: quadratic at genus~$0$; curved-central at genus~$g \geq 1$
on the Koszul locus; filtered-complete off it
\textup{(}cf.\ Convention~\textup{\ref{conv:regime-tags})}.]}

The Heisenberg inversion $\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{H}_k)) \xrightarrow{\sim} \mathcal{H}_k$ (\S\ref{sec:frame-inversion}) generalizes to all Koszul chiral algebras.

Let $\mathcal{A}$ be a \emph{Koszul} chiral algebra on a Riemann surface $X$
(Definition~\ref{def:chiral-koszul-pair}), with
$\bar{B}^{\mathrm{ch}}(\mathcal{A})$ conilpotent or $\mathcal{A}$ complete
with respect to its augmentation ideal
(\S\ref{sec:i-adic-completion}).  Then the natural map:
\[\psi: \Omega(\bar{B}(\mathcal{A})) \longrightarrow \mathcal{A}\]
induced by the bar-cobar adjunction is a \emph{quasi-isomorphism}, not merely
an isomorphism in cohomology.

More precisely:
\begin{enumerate}
\item The map $\psi$ is a morphism of chiral algebras (respects all structure)

\item At each genus $g$, the genus-$g$ component:
      \[\psi_g: \Omega_g(\bar{B}_g(\mathcal{A})) \longrightarrow \mathcal{A}\]
      is a quasi-isomorphism

\item The full genus-graded map:
      \[\psi = \bigoplus_{g=0}^\infty \psi_g: \Omega(\bar{B}(\mathcal{A})) \longrightarrow \mathcal{A}\]
      converges and is a quasi-isomorphism in the $\hbar$-adic completion

\item There exists a spectral sequence converging to $H^\bullet(\mathcal{A})$
      with $E_1$-page given by the bar-cobar complex; it collapses at $E_2$
      by the Koszul property (Theorem~\ref{thm:spectral-sequence-collapse})
\end{enumerate}

\smallskip\noindent\emph{Scope.}
The Koszul hypothesis is essential: for admissible-level affine algebras
and minimal-model Virasoro/W-algebras the bar spectral sequence has
nontrivial higher differentials and the counit $\psi$ is \emph{not} a
quasi-isomorphism (see Remark~\ref{rem:sl2-admissible}
and~\ref{rem:virasoro-module-koszul-minimal}).  In those regimes one must work
with the completed or coderived bar-cobar correspondence
(Corollary~\ref{cor:bar-cobar-inverse},
\S\ref{sec:i-adic-completion}).
\end{theorem}

\begin{proof}[Dependency-closed proof]
We verify each numbered clause by previously established results in this chapter.
\begin{enumerate}[label=(D\arabic*)]
\item \emph{Morphism of chiral algebras.}
The map $\psi$ is the counit of the bar-cobar adjunction from
Theorem~\ref{thm:bar-cobar-adjunction}; therefore it is canonical and respects
the algebraic structure by functoriality of bar and cobar
(Theorem~\ref{thm:bar-functorial}, Theorem~\ref{thm:cobar-functorial}).

\item \emph{Genuswise quasi-isomorphism.}
The genus-$0$ base case is proved independently by
Theorem~\ref{thm:bar-nilpotency-complete} and
Theorem~\ref{thm:chiral-koszul-duality};
equivalently, it is the implication
\ref{ftm:koszul}$\Rightarrow$\ref{ftm:counit} of
the fundamental theorem of chiral twisting morphisms
(Theorem~\ref{thm:fundamental-twisting-morphisms}).
The genus-$g$ components $\psi_g$ for $g \geq 1$ are quasi-isomorphisms by
induction on genus via
Theorem~\ref{thm:genus-graded-convergence}, item~(2), together with the
higher-genus inversion package (Theorem~\ref{thm:higher-genus-inversion}).

\item \emph{Full genus-graded convergence and quasi-isomorphism.}
This is Theorem~\ref{thm:genus-graded-convergence}, item (3), which identifies
the completed genus series $\psi=\sum_{g\ge 0}\hbar^{2g-2}\psi_g$ and proves convergence.

\item \emph{Spectral sequence statement.}
Existence and explicit page description are exactly
Theorem~\ref{thm:bar-cobar-spectral-sequence}; collapse for Koszul input is
Theorem~\ref{thm:spectral-sequence-collapse}.
\end{enumerate}
Combining (D1)--(D4) gives all four clauses of the theorem.
\end{proof}

\begin{remark}[Relation to the fundamental theorem \texorpdfstring{$\mathrm{A}_0$}{A_0}]
\label{rem:inversion-vs-fundamental}
At genus~$0$, Theorem~\ref{thm:bar-cobar-inversion-qi} is a
consequence of the fundamental theorem of chiral twisting morphisms
(Theorem~\ref{thm:fundamental-twisting-morphisms}):
the counit $\Omega_X(\bar{B}_X(\cA)) \to \cA$ being a
quasi-isomorphism is one of the four equivalent characterizations
of Koszulity established there.  The present theorem extends this
to all genera via the genus induction of clause~(D2).
\end{remark}

\begin{remark}[Quasi-isomorphism of chain complexes vs chiral algebras]\label{rem:qi-vs-homology-iso}
The distinction is between two levels of structure:

\emph{Chain complex quasi-isomorphism.} A chain map $\psi: C^\bullet \to D^\bullet$ inducing an isomorphism $H^\bullet(\psi): H^\bullet(C) \xrightarrow{\cong} H^\bullet(D)$ on cohomology. This is the standard notion; a ``homology isomorphism'' and a ``quasi-isomorphism'' are the \emph{same thing} at the chain complex level.

\emph{Chiral algebra quasi-isomorphism.} An $A_\infty$ (or chiral algebra) morphism $\psi\colon \mathcal{A} \to \mathcal{B}$ whose linear component $\psi_1\colon \mathcal{A} \to \mathcal{B}$ is a chain complex quasi-isomorphism. Such a map preserves the full $A_\infty$ structure up to coherent homotopy. The distinction matters:
A chain complex quasi-isomorphism tells us only about $H^\bullet$ and need not respect multiplicative or $A_\infty$ structure, whereas a chiral algebra quasi-isomorphism gives a full equivalence in the derived category of chiral algebras, preserving all homotopy-theoretic information.  For Koszul duality, the map $\Omega(B(\mathcal{A})) \to \mathcal{A}$ must be a quasi-isomorphism of \emph{chiral algebras}, not merely of chain complexes, to establish derived equivalences.

\emph{Example.}
Consider a dga $(C^\bullet, d, \mu)$ with:
\[\cdots \to 0 \to \mathbb{C} \xrightarrow{0} \mathbb{C} \to 0 \to \cdots\]

This has $H^0 = \mathbb{C}$, $H^i = 0$ for $i \neq 0$.

Compare with the algebra $(D^\bullet, 0, \nu) = (\mathbb{C}, 0, 0)$ in degree 0.
The projection $\pi: C^\bullet \to D^\bullet$ is a quasi-isomorphism of chain
complexes (both have $H^0 = \mathbb{C}$), but $\pi$ does \emph{not} respect the
multiplication ($\pi$ need not intertwine $\mu$ and $\nu$ at the chain level).
To obtain a quasi-isomorphism of \emph{algebras}, one must work with $A_\infty$
morphisms, which encode the higher homotopies relating the two multiplicative
structures.
\end{remark}

\subsection{Proof strategy and filtration}

\begin{definition}[Bar-cobar filtration]\label{def:bar-cobar-filtration}
Define a decreasing filtration on $\Omega(\bar{B}(\mathcal{A}))$ by:
\[F^p\Omega(\bar{B}(\mathcal{A})) = \bigoplus_{n \geq p} \Omega^n(\bar{B}^n(\mathcal{A}))\]

This is the filtration by \emph{bar degree} (= cobar arity).

\emph{Geometric meaning.} $F^p$ consists of elements involving at least $p$ points
in configuration space. As $p \to \infty$, we are considering increasingly complicated
configurations.

\emph{Properties.}
\begin{enumerate}
\item $F^0 \supseteq F^1 \supseteq F^2 \supseteq \cdots$
\item $\bigcap_{p=0}^\infty F^p = 0$ (completeness)
\item The differential respects filtration: $d(F^p) \subseteq F^p$
\item The natural map factors through the filtration
\end{enumerate}
\end{definition}

\begin{lemma}[Associated graded; \ClaimStatusProvedHere]\label{lem:bar-cobar-associated-graded}
The associated graded of the bar-cobar filtration is:
\[\text{Gr}^p\Omega(\bar{B}(\mathcal{A})) = \Omega^p(\bar{B}^p(\mathcal{A}))\]

The induced differential on $\text{Gr}^\bullet$ is the \emph{internal differential} $d_{\text{internal}}$ alone (i.e., the differential inherited from $\mathcal{A}$).
\end{lemma}

\begin{proof}
By definition of associated graded:
\[\text{Gr}^p = F^p / F^{p+1} = \Omega^p(\bar{B}^p(\mathcal{A}))\]

The full differential on $\Omega(\bar{B}(\mathcal{A}))$ decomposes as $d = d_{\text{internal}} + d_{\text{bar}} + d_{\text{cobar}}$, where $d_{\text{internal}}$ preserves the filtration degree (it acts within each tensor factor), $d_{\text{bar}}$ preserves or lowers filtration degree (collisions reduce arity), and $d_{\text{cobar}}$ raises filtration degree by~$1$ (comultiplication increases cobar arity).  On the associated graded $\text{Gr}^p = F^p/F^{p+1}$, only the \emph{filtration-preserving} component survives: $d_{\text{cobar}}$ maps $F^p$ into $F^{p+1}$ and so vanishes on $\text{Gr}^p$, while $d_{\text{bar}}$ maps $F^p$ into $F^{p-1} \subset F^p$ and so also acts trivially on $\text{Gr}^p$.  Thus $d_{\text{gr}} = d_{\text{internal}}$, which is the $d_0$ differential of the spectral sequence (cf.\ Theorem~\ref{thm:bar-cobar-spectral-sequence}).
\end{proof}

\subsection{Spectral sequence construction}

\begin{theorem}[Bar-cobar spectral sequence; \ClaimStatusProvedHere]\label{thm:bar-cobar-spectral-sequence}
\label{thm:koszul-spectral-sequence}
The filtration from Definition~\ref{def:bar-cobar-filtration} induces a spectral 
sequence:
\[E_0^{p,q} = \left(F^p / F^{p+1}\right)^{p+q} \implies H^{p+q}(\Omega(\bar{B}(\mathcal{A})))\]
converging to the cohomology of $\Omega(\bar{B}(\mathcal{A}))$.  Here $p$ is the filtration degree (cobar arity) and $q$ is the complementary degree (from the internal and bar gradings), so the total degree is $p + q$.

\emph{Explicit description of pages.}
\begin{align*}
E_0^{p,q} &= \left(F^p\Omega^{p+q}(\bar{B}(\mathcal{A})) \big/ F^{p+1}\Omega^{p+q}(\bar{B}(\mathcal{A}))\right) \quad \text{(associated graded)} \\
E_1^{p,q} &= H^{p+q}\!\left(E_0^{p,\bullet},\, d_{\text{internal}}\right)
            \quad \text{(internal cohomology at fixed cobar degree $p$)} \\
E_2^{p,q} &= H^p\!\left(E_1^{\bullet,q},\, d_{\text{bar}}\right)
            \quad \text{(bar cohomology)} \\
E_\infty^{p,q} &= \mathrm{Gr}^p H^{p+q}(\Omega(\bar{B}(\mathcal{A}))) \quad \text{(limiting page)}
\end{align*}
\end{theorem}

\begin{proof}
This is a standard spectral sequence associated to a filtered complex (Weibel~\cite{Weibel94}, Chapter~5).  We verify the key properties:

\emph{Step 1: $E_0$ page.} This is just the raw complex with its bigrading:
\[E_0^{p,q} = F^p\Omega^{p+q}(\bar{B}(\mathcal{A})) / F^{p+1}\Omega^{p+q}(\bar{B}(\mathcal{A}))\]

By definition of the filtration, this isolates the piece in cobar degree~$p$ and total degree $p+q$.

\emph{Step 2: $d_0$ differential.} On the $E_0$ page:
\[d_0: E_0^{p,q} \to E_0^{p,q+1}\]
is the \emph{internal differential} $d_{\text{internal}}$ (from the differential 
on $\mathcal{A}$ itself).

Taking cohomology gives the $E_1$ page.

\emph{Step 3: $d_1$ differential.} On the $E_1$ page:
\[d_1: E_1^{p,q} \to E_1^{p+1,q}\]
is induced by the \emph{bar differential} $d_{\text{bar}}$ (collisions in 
configuration space).

Taking cohomology gives the $E_2$ page.

\emph{Step 4: Higher differentials.} For $r \geq 2$:
\[d_r: E_r^{p,q} \to E_r^{p+r,q-r+1}\]

These differentials encode higher-order interactions between bar and cobar operations.

\emph{Step 5: Convergence.} The spectral sequence converges because:
\begin{enumerate}
\item The filtration is complete: $\bigcap_p F^p = 0$
\item The filtration is exhaustive: $\bigcup_p F^p = \Omega(\bar{B}(\mathcal{A}))$
\item The complex is bounded in each column (fixed $p$)
\end{enumerate}

By standard spectral sequence theory (Weibel \cite{Weibel94}, Chapter 5), this ensures:
\[E_\infty^{p,q} = \text{Gr}^p H^{p+q}(\Omega(\bar{B}(\mathcal{A})))\]
\end{proof}

\begin{theorem}[Collapse at \texorpdfstring{$E_2$}{E2}; \ClaimStatusProvedHere]\label{thm:spectral-sequence-collapse}
\textup{[Regime: quadratic, Koszul locus
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

For the Heisenberg algebra, the spectral sequence collapsed trivially because $d_{\mathrm{bracket}} = 0$ (no simple poles): the bar cohomology was concentrated in degrees $0$ and $2$ without further work (\S\ref{sec:frame-bar-all}).  For non-abelian algebras, the collapse is a consequence of the Koszul property.

For a Koszul chiral algebra $\mathcal{A}$ (Remark~\ref{rem:koszul-chiral}), the spectral sequence from
Theorem~\ref{thm:bar-cobar-spectral-sequence} collapses at the $E_2$ page:
\[E_2^{p,q} = E_\infty^{p,q}.\]
\end{theorem}

\begin{proof}
The Koszul property of $\mathcal{A}$ means that the natural inclusion $\iota: \mathcal{A}^! \hookrightarrow \bar{B}(\mathcal{A})$ of the quadratic dual into the bar complex is a quasi-isomorphism (see \cite[Theorem~3.4.1]{LV12} for the classical case and Chapter~\ref{chap:koszul-pairs} for the chiral adaptation). Since $\mathcal{A}^!$ is generated in weight~1 with quadratic relations, its image under $\iota$ lies on the diagonal $p + q = \text{const}$ in the bigrading $(p,q)$ by bar degree and internal degree.

At the $E_1$ page, we compute the cohomology of each column with respect to $d_0 = d_{\text{int}}$. The $E_1$ page of the bar-cobar spectral sequence is computed by the cohomology of the bar complex: each column $E_0^{p,\bullet}$ with its internal differential $d_0$ is precisely the bar complex $\bar{B}^p(\mathcal{A})$ in cobar degree~$p$, so $E_1^{p,q} = H^q(\bar{B}^p(\mathcal{A}), d_{\mathrm{int}})$. By the Koszul quasi-isomorphism, the bar cohomology is concentrated on the diagonal, giving $E_1^{p,q} = 0$ whenever $q \neq 0$ (after reindexing by the bar filtration degree).

At the $E_2$ page, we take cohomology with respect to $d_1$ (induced by $d_{\text{bar}}$). The $E_2$ groups inherit the diagonal concentration.

For $r \geq 2$, the differential $d_r: E_r^{p,q} \to E_r^{p+r, q-r+1}$ shifts the bidegree by $(r, 1-r)$. Since $E_2^{p,q} = 0$ for $q \neq 0$, either the source or the target of $d_r$ vanishes for every $r \geq 2$. Therefore $d_r = 0$ for all $r \geq 2$, and the spectral sequence collapses at $E_2$.
\end{proof}

\subsection{Convergence at all genera}

\begin{theorem}[Genus-graded convergence; \ClaimStatusProvedHere]\label{thm:genus-graded-convergence}
\textup{[Regime: curved-central on the Koszul locus
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

Let $\mathcal{A}$ be a Koszul chiral algebra satisfying the hypotheses of
Theorem~\ref{thm:bar-cobar-inversion-qi}.  The bar-cobar inversion
$\psi: \Omega(\bar{B}(\mathcal{A})) \to \mathcal{A}$
converges at each genus $g$, and the full genus-graded sum converges in the
$\hbar$-adic completion.

More precisely:
\begin{enumerate}
\item \emph{Genus zero:} 
      \[\psi_0: \Omega_0(\bar{B}_0(\mathcal{A})) \xrightarrow{\sim} \mathcal{A}\]
      is a quasi-isomorphism (classical result, BD §3.7)
      
\item \emph{Fixed genus $g$:}
      \[\psi_g: \Omega_g(\bar{B}_g(\mathcal{A})) \to \mathcal{A}_g\]
      is a quasi-isomorphism after appropriate quantum corrections (here $\mathcal{A}_g$ denotes the genus-$g$ component of the genus-graded chiral algebra)
      
\item \emph{Genus series:}
      \[\psi = \sum_{g=0}^\infty \hbar^{2g-2} \psi_g\]
      converges in the $\hbar$-adic completion for $|\hbar| < R$ (radius determined 
      by growth of moduli spaces)
\end{enumerate}
\end{theorem}

\begin{proof}
We prove each case separately.

\emph{Case 1: Genus zero (classical).}

At genus zero, we work with rational curves $\mathbb{P}^1$. The bar complex is:
\[\bar{B}_0^n(\mathcal{A}) = \Gamma\left(\overline{C}_n(\mathbb{P}^1), 
\mathcal{A}^{\boxtimes n} \otimes \Omega^\bullet\right)\]

Beilinson--Drinfeld proved \cite{BD04} Theorem 3.7.11:
\[\Omega_0(\bar{B}_0(\mathcal{A})) \xrightarrow{\sim} \mathcal{A}\]

Their proof uses:
\begin{itemize}
\item Chevalley--Cousin resolution
\item Ran space formalism
\item Descent from configuration spaces
\end{itemize}

We have verified (Theorem~\ref{thm:BD-extension-higher-genus}) that all technical 
conditions hold at genus zero.

\emph{Case 2: Fixed genus $g \geq 1$.}

At higher genus, configuration spaces fiber over moduli space:
\[\pi: \overline{C}_n(X) \to \overline{\mathcal{M}}_g\]

The bar complex becomes:
\[\bar{B}_g^n(\mathcal{A}) = R\pi_*\left(\mathcal{A}^{\boxtimes n} \otimes \Omega^\bullet_{\log}\right)\]
(equivalently, $\int_{\overline{\mathcal{M}}_{g,n}} \mathcal{A}^{\boxtimes n} \otimes \Omega^\bullet_{\log}$ in the factorization homology notation of Lemma~\ref{lem:bar-as-fact-hom-AF}).

The pushforward $\pi_*$ preserves quasi-isomorphisms:

\begin{lemma}[Derived pushforward preserves QI; \ClaimStatusProvedHere]\label{lem:pushforward-preserves-qi}
For a proper morphism $\pi: Y \to Z$ and a quasi-isomorphism $f: \mathcal{F} \xrightarrow{\sim} \mathcal{G}$
of bounded-below complexes of sheaves on $Y$, the derived pushforward:
\[R\pi_*(f): R\pi_*\mathcal{F} \xrightarrow{\sim} R\pi_*\mathcal{G}\]
is a quasi-isomorphism in $D^+(Z)$.
\end{lemma}

\begin{proof}[Proof of Lemma]
Since $R\pi_*$ is a derived functor, it preserves quasi-isomorphisms by definition (a quasi-isomorphism between complexes of sheaves becomes an isomorphism in the derived category, and $R\pi_*$ is a functor on derived categories).  The underived $\pi_*$ does \emph{not} preserve quasi-isomorphisms in general.

In our application, the complexes involved are complexes of locally free sheaves on smooth proper varieties, so the Leray spectral sequence $H^p(Z, R^q\pi_*\mathcal{F}) \Rightarrow H^{p+q}(Y, \mathcal{F})$ applies, and the statement follows from the proper base change theorem.
\end{proof}

Applying this lemma: Since $\psi$ is a quasi-isomorphism fiberwise (over each
point of $\overline{\mathcal{M}}_g$), the derived pushforward $R\pi_*(\psi)$ is also a quasi-isomorphism (the FM compactification $\overline{C}_n(X)$ is proper over $\overline{\mathcal{M}}_g$, and the complexes are bounded, so proper base change applies).

\emph{Quantum corrections.} At genus $g \geq 1$, we must account for:
\begin{itemize}
\item Central charge contributions: $\sim \int_{\overline{\mathcal{M}}_g} \lambda_1$ 
      (Hodge class)
\item Modular form corrections: Period integrals over $H^1(\Sigma_g)$
\item Anomaly cancellation: Ensures $\dfib^{\,2} = 0$ (fiberwise nilpotence)
\end{itemize}

With these corrections included (see Theorem~\ref{thm:higher-genus-inversion}), 
$\psi_g$ is a quasi-isomorphism.

\emph{Case 3: Genus series convergence.}

Consider the formal series:
\[\psi(\hbar) = \sum_{g=0}^\infty \hbar^{2g-2} \psi_g\]

\emph{Growth estimate.} By Mirzakhani's results \cite{Mirzakhani}, Weil--Petersson volumes satisfy
\[\mathrm{Vol}(\overline{\mathcal{M}}_g) \sim (2g)!\]
with factorial growth.  Consequently the formal genus series has zero radius of analytic convergence, consistent with the non-Borel-summability of the perturbative string expansion.

\emph{$\hbar$-adic completion.} For rigorous formal computations, work in:
\[\widehat{\Omega}(\bar{B}(\mathcal{A}))_\hbar = \varprojlim_n 
\Omega(\bar{B}(\mathcal{A})) / \hbar^n\]

In this completion, the series converges unconditionally.
\end{proof}

\subsection{The counit of the adjunction}

\begin{proposition}[Counit is quasi-isomorphism; \ClaimStatusProvedHere]\label{prop:counit-qi}
The counit of the bar-cobar adjunction:
\[\epsilon: \bar{B}(\Omega(\mathcal{C})) \longrightarrow \mathcal{C}\]
for a chiral coalgebra $\mathcal{C}$ is also a quasi-isomorphism (dual statement).
\end{proposition}

\begin{proof}
By Verdier duality (Theorem~\ref{thm:verdier-bar-cobar}), the counit $\epsilon_{\mathcal{C}} \colon \bar{B}^{\mathrm{ch}}(\Omega^{\mathrm{ch}}(\mathcal{C})) \to \mathcal{C}$ is the Verdier dual of the unit $\eta_{\mathcal{A}^!}$, which is a quasi-isomorphism by Theorem~\ref{thm:geom-unit}.  Since Verdier duality on the Fulton--MacPherson compactifications preserves quasi-isomorphisms (Theorem~\ref{thm:verdier-bar-cobar}), the result follows.
\end{proof}

\subsection{Functoriality of the quasi-isomorphism}

\begin{theorem}[Functoriality; \ClaimStatusProvedHere]\label{thm:bar-cobar-inversion-functorial}
\label{thm:cobar-functorial}
The quasi-isomorphism $\psi: \Omega(\bar{B}(\mathcal{A})) \xrightarrow{\sim} \mathcal{A}$ 
is \emph{functorial}: for any morphism $f: \mathcal{A} \to \mathcal{A}'$ of 
chiral algebras, the diagram commutes:

\begin{center}
\begin{tikzcd}
\Omega(\bar{B}(\mathcal{A})) \ar[r, "\psi"] \ar[d, "\Omega(\bar{B}(f))"] 
& \mathcal{A} \ar[d, "f"] \\
\Omega(\bar{B}(\mathcal{A}')) \ar[r, "\psi'"] 
& \mathcal{A}'
\end{tikzcd}
\end{center}
\end{theorem}

\begin{proof}
This follows from the functoriality of the bar construction (Theorem~\ref{thm:bar-functorial}) and the universal property of the bar-cobar adjunction (Theorem~\ref{thm:bar-cobar-adjunction}).

\emph{Step 1:} The bar construction is functorial:
\[\bar{B}(f): \bar{B}(\mathcal{A}) \to \bar{B}(\mathcal{A}')\]

\emph{Step 2:} The cobar construction is functorial:
\[\Omega(g): \Omega(\mathcal{C}) \to \Omega(\mathcal{C}')\]
for any coalgebra morphism $g$.

\emph{Step 3:} The natural transformation $\psi$ is defined universally via the 
adjunction, hence commutes with all morphisms.

\emph{Step 4:} At each genus, $\psi_g$ is natural in $\mathcal{A}$, so the 
genus-graded sum is also natural.
\end{proof}

\subsection{Applications to derived equivalences}

\begin{corollary}[Derived equivalence; \ClaimStatusProvedHere]\label{cor:derived-equivalence-bar-cobar}
\label{cor:derived-equivalence-koszul}
Let $\mathcal{A}$ be a Koszul chiral algebra on a smooth curve $X$ with Koszul dual
coalgebra $\mathcal{A}^!$.  Make the following assumptions:
\begin{enumerate}[label=(\roman*)]
\item $\mathcal{A}$ is augmented over $\mathcal{O}_X$ and locally finitely generated
as a $\mathcal{D}_X$-module.
\item ``Module'' means \emph{chiral module} in the sense of Beilinson--Drinfeld
\cite{BD04}: a $\mathcal{D}_X$-module $M$ with a chiral action map
$\mu_M: j_*j^*(\mathcal{A} \boxtimes M) \to \Delta_! M$.
\item ``Comodule'' means a conilpotent $\mathcal{A}^!$-comodule
$N$ with coaction $\Delta_N: N \to \mathcal{A}^! \chirtensor N$ satisfying
the usual coassociativity and counit axioms.
\item The derived categories $\mathcal{D}^b$ are the bounded derived categories
of complexes with finitely generated cohomology.
\end{enumerate}
Under these hypotheses, the bar and cobar constructions induce an equivalence
of triangulated categories:
\[\mathcal{D}^b(\text{Mod}^{\mathrm{fg}}(\mathcal{A})) \simeq
\mathcal{D}^b(\text{Comod}^{\mathrm{conil}}(\mathcal{A}^!))\]
via the functors $\bar{B}(-) = \mathcal{A}^! \otimes^{\tau}_{\mathcal{A}} (-)$
(bar extension of scalars) and $\Omega(-) = \mathcal{A} \otimes^{\tau}_{\mathcal{A}^!} (-)$
(cobar extension of scalars), where $\tau: \mathcal{A}^! \to \mathcal{A}$ is the
universal twisting cochain.
\end{corollary}

\begin{proof}
The quasi-isomorphisms $\psi: \Omega(\bar{B}(\mathcal{A})) \xrightarrow{\sim} \mathcal{A}$
and $\epsilon: \bar{B}(\Omega(\mathcal{A}^!)) \xrightarrow{\sim} \mathcal{A}^!$
establish:

\begin{center}
\begin{tikzcd}
\text{Mod}^{\mathrm{fg}}(\mathcal{A}) \ar[r, "\bar{B}", shift left=1ex]
& \text{Comod}^{\mathrm{conil}}(\mathcal{A}^!) \ar[l, "\Omega", shift left=1ex]
\end{tikzcd}
\end{center}

with $\Omega \circ \bar{B} \simeq \text{id}$ and $\bar{B} \circ \Omega \simeq \text{id}$
up to quasi-isomorphism.  The finiteness hypothesis~(i) ensures the bar construction
preserves bounded complexes; the conilpotence hypothesis~(iii) ensures the cobar
construction converges.  Together these give the stated equivalence on derived categories.
\end{proof}

\begin{remark}[Scope and limitations]\label{rem:derived-equiv-scope}
The hypotheses above are essential:
\begin{itemize}
\item Without finite generation, the bar construction may produce unbounded complexes.
\item Without conilpotence, the cobar series $\Omega(\mathcal{A}^!) = \bigoplus_{n \geq 1}
\mathcal{A}^{!\otimes n}$ may not converge, and the functor $\Omega$ is not well-defined.
\item For non-quadratic algebras, one must replace $\mathcal{A}^!$ by its nilpotent
completion (Appendix~\ref{app:nilpotent-completion}) and work with pro-nilpotent
comodules.
\end{itemize}
Even in ordinary algebra, Koszul duality yields equivalences between
\emph{specific subcategories}, not the entire derived category without
finiteness conditions; cf.~Beilinson--Ginzburg--Soergel \cite{BGS96}.
\end{remark}

\begin{remark}[Physical significance]\label{rem:qi-matters-physics}
From the physics perspective, the distinction between homology isomorphism and 
quasi-isomorphism corresponds to:

A homology isomorphism gives only on-shell equivalence: physical states match, but one cannot compute scattering amplitudes or access quantum corrections.  A full quasi-isomorphism gives off-shell equivalence: the entire QFT matches, correlation functions and amplitudes are computable, quantum corrections are encoded in the higher homotopies, and the path integral measure is determined.  This is why establishing the quasi-isomorphism---not just the homology isomorphism---is essential for physical applications.
\end{remark}

%================================================================
% RECOGNIZING KOSZUL DUALS IN PRACTICE
%================================================================

\section{Recognizing Koszul duals in practice}
\label{sec:recognizing-koszul-duals}

\begin{remark}[Identifying \texorpdfstring{$\mathcal{A}^!$}{A!} in practice]\label{rem:identify-koszul-wild}
When encountering a coalgebra $\widehat{\mathcal{C}}$ in geometry or physics, use 
the following checklist to determine if it is a Koszul dual:

\emph{Step 1: Check necessary conditions} (Theorem~\ref{thm:essential-image-koszul}):
\begin{itemize}
\item[$\square$] Conilpotent? ($\bigcap_n \text{coker}(\Delta^n) = 0$)
\item[$\square$] Connected? ($\epsilon: \widehat{\mathcal{C}} \twoheadrightarrow \mathbb{C}$)
\item[$\square$] Geometrically representable? (arises from configuration spaces)
\item[$\square$] Curvature central? (if curved)
\item[$\square$] Formally complete? (with respect to coaugmentation)
\end{itemize}

\emph{Step 2: Compute candidate algebra:}
\[\mathcal{A}_{\text{candidate}} = \Omega(\widehat{\mathcal{C}})\]

\emph{Step 3: Verify bar-cobar inversion:} Compute $\bar{B}(\mathcal{A}_{\text{candidate}})$ and check if $\bar{B}(\mathcal{A}_{\text{candidate}}) \simeq \widehat{\mathcal{C}}$.

\emph{Step 4: If yes:}
\[\widehat{\mathcal{C}} = \mathcal{A}_{\text{candidate}}^!\]

\emph{Examples where this works.}
\begin{itemize}
\item Heisenberg coalgebra $\to$ Heisenberg algebra
\item Exterior coalgebra $\to$ Free fermion $\beta\gamma$
\item Langlands dual Kac--Moody $\to$ Original Kac--Moody
\item Certain W-algebra coalgebras $\to$ W-algebras at special central charges
\end{itemize}

\emph{Examples where this fails:} non-conilpotent coalgebras (cannot be Koszul duals) and geometrically non-representable coalgebras (not from configuration spaces).
\end{remark}

\section{The Ran-space perspective}
\label{sec:ran-space-perspective}
\index{Ran space!bar-cobar perspective}

The $\infty$-categorical framework of factorization
algebras on $\operatorname{Ran}(X)$ provides the conceptual home for
the bar-cobar adjunction.

\begin{remark}[From configuration spaces to Ran space]\label{rem:config-to-ran}
The configuration spaces $C_n(X)$ and their FM compactifications
$\overline{C}_n(X)$ are finite-dimensional approximations to the
\emph{Ran space} $\operatorname{Ran}(X) = \operatorname{colim}_n\,
X^n / \Sigma_n$, the space of all finite non-empty subsets of~$X$.
The bar complex $\bar{B}(\cA) = \bigoplus_n \bar{B}^n(\cA)$, with
$\bar{B}^n(\cA)$ living on $\overline{C}_n(X)$, assembles into a
single object on $\operatorname{Ran}(X)$.  The bar differential,
given by residues at collision divisors
(Definition~\ref{def:bar-differential-complete}), becomes the
factorization structure map: when two points collide, the OPE
produces the ``fusion'' of the corresponding tensor factors.

In this language, the Arnold relations that ensure $d^2 = 0$
(Theorem~\ref{thm:bar-nilpotency-complete}) are the coherence conditions
for the factorization algebra axiom: the result of a three-point
collision does not depend on the order in which pairs collide,
because the relevant boundary strata of $\overline{C}_3(X)$ are
related by the Arnold relation
$\omega_{12} \wedge \omega_{23} + \omega_{23} \wedge \omega_{31}
+ \omega_{31} \wedge \omega_{12} = 0$.
\end{remark}

\begin{remark}[Verdier duality as the engine of Koszul duality]\label{rem:verdier-engine}
\index{Verdier duality!Koszul duality engine}
The bar-cobar adjunction
\[
\bar{B}_X \colon
\operatorname{Alg}_{\mathrm{aug}}(\operatorname{Fact}(X))
\;\rightleftarrows\;
\operatorname{CoAlg}_{\mathrm{conil}}(\operatorname{Fact}(X))
\,:\!\Omega_X
\]
is controlled by Verdier duality on $\operatorname{Ran}(X)$.
The key identification is:
\[
\mathbb{D}_{\operatorname{Ran}} \bar{B}_X(\cA) \;\simeq\; \bar{B}_X(\cA^!).
\]
At the chain level, this identity is the content of
Theorem~\ref{thm:bar-cobar-isomorphism-main}: the Verdier dual of the
bar construction of $\cA$ is the bar construction of the Koszul dual
$\cA^!$.  The FM propagator $\omega_{ij}$ and its Verdier dual
$\omega_{ij}^\vee$ implement this duality on configuration spaces:
the propagator mediates the passage from algebra to coalgebra, and
Verdier duality exchanges the two.

This perspective makes the Poincar\'e--Koszul duality of
Ayala--Francis~\cite{AF15} manifest: their equivalence
$\int_M A \simeq (\int_{-M} A^!)^\vee$ is the shadow, at the level
of factorization homology, of the chain-level Verdier identification
above.
\end{remark}

\begin{remark}[Curvature and coderived categories]\label{rem:curvature-coderived}
\index{coderived category!bar-cobar}
\index{curvature!coderived category}
When curvature is present---i.e., when the genus-$1$ obstruction
$m_0^{(1)} = \kappa(\cA) \neq 0$ (as it does for all non-trivial
Koszul chiral algebras; see
Theorem~\ref{thm:genus-universality})---the bar complex satisfies
$\dfib^{\,2} = \kappa \cdot \omega_1 \cdot \mathrm{id}$ rather than $\dfib^{\,2} = 0$
(see Convention~\ref{conv:higher-genus-differentials} for the notation).
The ordinary derived category of $\cA$-modules is then the wrong
quotient: it erases the distinction between ``acyclic because of
$\dfib^{\,2} \neq 0$'' and ``acyclic because of genuine exactness.''

The correct ambient category is the \emph{coderived category}
$\mathcal{D}^{\mathrm{co}}(\cA)$ in the sense of
Positselski~\cite{Positselski11}.  In this category, a curved complex
$(M, d_M)$ with $d_M^2 = \kappa \cdot \mathrm{id}_M$ is
\emph{not} set to zero; it represents a genuine object encoding the
curvature.  The bar-cobar adjunction lifts to an equivalence
\[
\bar{B}_X \colon
\mathcal{D}^{\mathrm{co}}(\operatorname{Mod}(\cA))
\;\simeq\;
\mathcal{D}^{\mathrm{ctr}}(\operatorname{Comod}(\cA^!))
\]
between the coderived category of modules and the contraderived category
of comodules.  On the Koszul locus---where the curvature vanishes or
is absorbed into the differential---the coderived and derived categories
agree, and the equivalence reduces to
Corollary~\ref{cor:derived-equivalence-koszul}.  Off this locus, the
coderived formalism captures the ``acyclic-but-not-contractible''
phenomena that higher-genus curvature creates.

This perspective clarifies the physical meaning of curvature: the
cosmological constant $\Lambda \sim \kappa(\cA)$ in the AdS$_3$/CFT$_2$
correspondence (Conjecture~\ref{conj:ads-cft-bar}) is the obstruction
to reducing the coderived category to the derived category.  Anomaly
cancellation at $c = 26$ ($\kappa = 0$) is precisely the condition
under which the coderived and derived categories agree, i.e., under
which the string theory is ``on-shell'' in the derived-categorical
sense.
\end{remark}

The bar-cobar adjunction for chiral algebras is now fully constructed:
the bar differential is a residue on Fulton--MacPherson
compactifications, $d^2 = 0$ follows from the Arnold relations, and
Verdier duality on $\operatorname{Ran}(X)$ intertwines bar and cobar
(Theorem~\ref{thm:verdier-bar-cobar}).  For Koszul pairs, the
adjunction is an equivalence (Theorem~\ref{thm:bar-cobar-isomorphism-main}).
This is the genus-$0$ theory.  Everything built so far lives on
configuration spaces of the fixed curve~$X$, with no reference to
moduli of curves.

\subsection{Bar-cobar as factorization homology}
\label{subsec:bar-cobar-fh}

The Ran-space remarks above assemble the bar complex into an
object on $\operatorname{Ran}(X)$.  We now show that this
assembly is not a reformulation but an \emph{identification}:
the bar construction \emph{is} factorization homology, and the
bar-cobar adjunction \emph{is} the adjunction of factorization
(co)homology functors.

\begin{proposition}[Bar construction as factorization homology;
\ClaimStatusProvedHere]
\label{prop:bar-fh}
\index{factorization homology!bar construction}
\index{bar construction!as factorization homology}
Let $\cA$ be an augmented $\Eone$-chiral algebra on a smooth
curve~$X$, and let $\overline{\cA} = \ker(\epsilon \colon \cA \to k)$
be the augmentation ideal.  Then there is a natural equivalence
\[
\Bbar^{\mathrm{geom}}_X(\cA)
\;\simeq\;
\int_X \overline{\cA}^{\mathrm{Lie}}
\]
where $\overline{\cA}^{\mathrm{Lie}}$ denotes $\overline{\cA}$ viewed as
an $\Eone$-Lie algebra via the commutator bracket, and the right-hand
side is factorization homology in the sense of
\textup{\cite{AF15, BD04}}.  More precisely:
\begin{enumerate}[label=(\roman*)]
\item \textbf{Finite approximations}: For each $n \geq 1$,
the degree-$n$ piece $\Bbar^n_X(\cA) =
(s^{-1}\overline{\cA})^{\otimes n}_{\overline{C}_n(X)}$
(the bar complex on~$n$ points, supported on the
Fulton--MacPherson compactification $\overline{C}_n(X)$) is the
restriction of the factorization homology $\int_X\overline{\cA}$
to $n$-point configurations.
\item \textbf{Assembly}: The bar differential
$d_{\mathrm{bar}} = \sum_{i < j} d_{ij}$ (residue along collision
divisors, Definition~\ref{def:bar-differential-complete}) is the
structure map of the factorization algebra:
the collision $z_i \to z_j$ implements the factorization product
$\int_{U_i}\overline{\cA} \otimes
\int_{U_j}\overline{\cA} \to
\int_{U_i \cup U_j}\overline{\cA}$
for shrinking discs $U_i \ni z_i$, $U_j \ni z_j$.
\item \textbf{Colimit}: The total bar complex
$\Bbar_X(\cA) = \bigoplus_{n \geq 0}\Bbar^n_X(\cA)$
is the colimit over $n$ of the finite approximations,
i.e., the factorization homology
$\int_X\overline{\cA} = \operatorname{colim}_{S \in
\mathrm{Fin}_{/X}} \bigotimes_{s \in S}\overline{\cA}_s$.
\end{enumerate}
\end{proposition}

\begin{proof}
The factorization homology of an $E_n$-algebra $A$ on a manifold
$M$ is defined as
\[
\textstyle\int_M A \;=\; \operatorname{colim}_{U_1 \sqcup \cdots
\sqcup U_k \hookrightarrow M} A(U_1) \otimes \cdots
\otimes A(U_k)\,,
\]
where the colimit is over rectilinear embeddings of disjoint discs
\cite[Definition~3.1]{AF15}.  For $n = 1$ on a curve~$X$, this is
the colimit over configurations of disjoint discs
$D_1 \sqcup \cdots \sqcup D_k \hookrightarrow X$, with
$A(D_i) = \overline{\cA}_{z_i}$ (the fiber of $\overline{\cA}$
at the center $z_i$ of $D_i$).

Part (i): The term $\Bbar^n_X(\cA)$ places one copy of
$s^{-1}\overline{\cA}$ at each of $n$ distinct points
$z_1, \ldots, z_n \in X$.  The locus of distinct points is the
open configuration space $C_n(X) = X^n \smallsetminus \Delta$,
and the extension to $\overline{C}_n(X)$ encodes the factorization
product at coincident points.

Part (ii): When $z_i \to z_j$, the factorization structure map
composes the two copies of $\overline{\cA}$ using the chiral
product.  At the chain level, this composition is the OPE residue
$\mathrm{Res}_{z_i = z_j}(\mu^{\mathrm{ch}}(\bar{a}_i, \bar{a}_j)
\cdot \omega_{ij})$, which is exactly the bar differential $d_{ij}$.

Part (iii): The colimit over $n$ in the bar complex is the colimit
over the category $\mathrm{Fin}_{/X}$ of finite subsets of $X$,
which is the Ran space $\operatorname{Ran}(X) =
\operatorname{colim}_n X^n/\Sigma_n$.  The factorization homology
$\int_X\overline{\cA}$ is this colimit by definition.
\end{proof}

\begin{proposition}[Cobar as factorization cohomology;
\ClaimStatusProvedHere]
\label{prop:cobar-fh}
\index{factorization homology!cobar construction}
\index{cobar construction!as factorization cohomology}
The cobar construction $\Omega_X(\cC)$ of a conilpotent
$\Eone$-chiral coalgebra $\cC$ is naturally equivalent to the
\emph{factorization cohomology}:
\[
\Omega_X(\cC) \;\simeq\;
\mathbb{R}\mathrm{Hom}_{\operatorname{Fact}(X)}
\bigl(k,\, \cC\bigr)
\;=:\;
\int^X \cC\,,
\]
the derived internal hom from the unit factorization algebra $k$
to~$\cC$ in the $\infty$-category of factorization coalgebras on~$X$.
Under Verdier duality $\mathbb{D}_{\mathrm{Ran}}$, this becomes:
\[
\Omega_X(\cC)
\;\simeq\;
\Bigl(\int_X \mathbb{D}_{\mathrm{Ran}}(\cC)\Bigr)^{\!\vee}\,,
\]
the linear dual of the factorization homology of the Verdier dual.
For $\cC = \Bbar_X(\cA)$, this gives
\[
\Omega_X\Bbar_X(\cA) \;\simeq\;
\Bigl(\int_X \Bbar_X(\cA^!)\Bigr)^{\!\vee}\,,
\]
which identifies the bar-cobar counit $\psi \colon
\Omega_X\Bbar_X(\cA) \to \cA$ with the Poincar\'e--Koszul duality
map of Ayala--Francis~\textup{\cite{AF15}}.
\end{proposition}

\begin{proof}
The cobar construction $\Omega_X(\cC) = T(s^{-1}\,\overline{\cC})$ with
differential $d_{\mathrm{cobar}} = d_{\mathrm{coop}} +
d_{\mathrm{tw}}$ is the free algebra on $s^{-1}\,\overline{\cC}$, with
the differential encoding the coalgebra structure of~$\cC$.
The free algebra on a module $V$ is
$\mathbb{R}\mathrm{Hom}(k, T^c(V))$, and for
$V = s^{-1}\,\overline{\cC}$ supported on $\operatorname{Ran}(X)$, this
is the factorization cohomology $\int^X\cC$ by
\cite[Proposition~5.5.2.5]{HA}.

The Verdier duality identification follows from
$\mathbb{D}_{\mathrm{Ran}}(\Bbar_X(\cA)) \simeq \Bbar_X(\cA^!)$
(Theorem~\ref{thm:verdier-bar-cobar}) and the general adjunction
$\mathrm{Hom}(k, \cC) \simeq (\int_X \mathbb{D}\cC)^\vee$.
The identification with Poincar\'e--Koszul duality follows from
\cite[Theorem~4.13]{AF15}: their equivalence
$\int_M A \simeq (\int_{-M} A^\vee)^\vee$ is precisely the
composition of Verdier duality on $\operatorname{Ran}(X)$ with
the bar-cobar adjunction.
\end{proof}

\begin{remark}[The bar-cobar adjunction as a duality of integration
theories]
\label{rem:bar-cobar-integration}
\index{factorization homology!duality of integration theories}
Propositions~\ref{prop:bar-fh} and~\ref{prop:cobar-fh} together
identify the bar-cobar adjunction
\[
\Bbar_X \colon
\operatorname{Alg}_{\mathrm{aug}}(\operatorname{Fact}(X))
\;\rightleftarrows\;
\operatorname{CoAlg}_{\mathrm{conil}}(\operatorname{Fact}(X))
\,:\!\Omega_X
\]
as the adjunction between two integration theories:
\begin{itemize}
\item The bar functor $\Bbar_X$ is \emph{factorization integration}:
it computes $\int_X(\cdot)$ by summing over configurations of
points on~$X$, with the OPE providing the integrand.
\item The cobar functor $\Omega_X$ is \emph{factorization
co-integration}: it computes $\int^X(\cdot)$ by taking the
internal hom from the unit, with the coproduct providing the
``inverse transform.''
\item Koszul duality $\cA \mapsto \cA^!$ is the
\emph{Verdier transform} mediating between the two:
$\Bbar(\cA)$ and $\Bbar(\cA^!)$ are Verdier dual, so the
bar of one algebra is the co-integration data for the dual.
\end{itemize}

This perspective reveals the bar-cobar machine as a
\emph{nonlinear Fourier duality} (cf.\
Remark~\ref{rem:koszul-fourier} and
Chapter~\ref{ch:en-koszul-duality}): the OPE kernel
$\omega_{ij} = d\log(z_i - z_j)$ plays the role of the Fourier
kernel $e^{2\pi i x\xi}$, the bar construction is the ``forward
transform'' (integration against the kernel), and the cobar is the
``inverse transform.''  Koszulness is the condition that the
transform is invertible (Fourier inversion), and the bar-cobar
counit $\Omega\Bbar(\cA) \to \cA$ is the Fourier inversion formula.
\end{remark}

\begin{remark}[The master diagram at genus~\texorpdfstring{$0$}{0}]
\label{rem:master-diagram-genus0}
\index{master diagram!genus zero}
The results of this chapter instantiate the master
diagram~\eqref{eq:master-square} at genus~$0$:
\[
\begin{tikzcd}[row sep=large, column sep=large]
\cA \arrow[r, "\barB_X"] \arrow[d, "(\cdot)^!"']
& \barB_X(\cA) \arrow[d, "\mathbb{D}_{\mathrm{Ran}}"] \\
\cA^! \arrow[r, "\barB_X"']
& \barB_X(\cA^!)
\end{tikzcd}
\]
The top row is the bar construction of this chapter; the right
column is Verdier duality
(Theorem~\ref{thm:verdier-bar-cobar}); the commutativity
$\mathbb{D}_{\mathrm{Ran}}\barB_X(\cA) \simeq \barB_X(\cA^!)$
is Theorem~A.  The cobar functor $\Omega_X$ is left adjoint
to~$\barB_X$, and the counit
$\Omega_X\barB_X(\cA) \xrightarrow{\sim} \cA$ is an
equivalence for Koszul algebras.

In the nilpotence-periodicity framework
(Remark~\ref{rem:nilpotence-periodicity}), this is the
\emph{single-valued regime} of the categorical logarithm:
$d^2 = 0$ exactly (the Arnold relations give single-valuedness),
so the logarithm has no monodromy and the diagram commutes
strictly.  At genus~$g \geq 1$
(Chapter~\ref{chap:higher-genus}), the logarithm acquires
monodromy---the square acquires
curvature~$\kappa(\cA) \cdot \omega_g$---and strict commutativity
is replaced by commutativity in the coderived category:
the passage from genus~$0$ to genus~$g$ is the passage from
single-valued to multi-valued logarithm, and the coderived
category is the analytic continuation that makes the multi-valued
logarithm well-defined.

The factorization homology perspective
(Propositions~\ref{prop:bar-fh},~\ref{prop:cobar-fh}) upgrades the
diagram from a commutative square of chain complexes to a
commutative square of \emph{factorization algebra objects} on
$\operatorname{Ran}(X)$.  The Verdier duality
$\mathbb{D}_{\mathrm{Ran}}$ becomes an $\infty$-categorical
involution, and the commutativity is an equivalence of factorization
algebras, not merely a quasi-isomorphism.  This
$\infty$-categorical enhancement is the H-level datum that
organizes the M-level constructions.
\end{remark}

\section{The categorical logarithm}
\label{sec:categorical-logarithm}
\index{categorical logarithm|textbf}
\index{nilpotence-periodicity correspondence!categorical logarithm}

The constructions of this chapter---bar, cobar, Verdier intertwining,
bar-cobar inversion, factorization homology---are not independent
results.  They are aspects of a single structure: the
\emph{categorical logarithm} for factorization algebras on algebraic
curves.  In this section we develop this identification
systematically, extracting from it both the conceptual unity of the
four main theorems and concrete predictions for higher-genus theory.

\subsection{The exponential-logarithm correspondence}
\label{subsec:exp-log-correspondence}

\begin{definition}[Categorical logarithm and exponential]
\label{def:categorical-log-exp}
\index{categorical logarithm!definition}
\index{categorical exponential!definition}
Let $\cA$ be an augmented $\Eone$-chiral algebra on a smooth
curve~$X$.  The \emph{categorical logarithm} of~$\cA$ is the bar
construction
\[
\log^{\mathrm{cat}}(\cA) \;:=\; \barB_X(\cA)\,,
\]
viewed as a factorization coalgebra on $\operatorname{Ran}(X)$
(Proposition~\ref{prop:bar-fh}).  The \emph{categorical exponential}
is the cobar construction
\[
\exp^{\mathrm{cat}}(\cC) \;:=\; \Omega_X(\cC)\,,
\]
viewed as a factorization algebra on $\operatorname{Ran}(X)$
(Proposition~\ref{prop:cobar-fh}).
\end{definition}

This terminology is justified by the following dictionary, each entry
of which is a theorem proved in this chapter or in
Chapter~\ref{chap:higher-genus}:

\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{p{5.5cm}p{5.5cm}}
\textbf{Classical logarithm} & \textbf{Categorical logarithm} \\
\hline
$\log \colon (\mathbb{C}^\times, \cdot) \to (\CC, +)$ &
$\barB \colon \mathrm{Alg}_{\mathrm{aug}} \to \mathrm{CoAlg}_{\mathrm{conil}}$ \\[2pt]
Maps multiplicative to additive &
Maps OPE (multiplicative) to bar differential (nilpotent/additive) \\[2pt]
$\exp(\log(z)) = z$ on convergence disk &
$\Omega(\barB(\cA)) \xrightarrow{\sim} \cA$ on Koszul locus
(Theorem~\ref{thm:bar-cobar-inversion-qi}) \\[2pt]
Power series $\log(1+z) = z - z^2/2 + \cdots$ &
PBW spectral sequence:
$E_1^{p,q} = H^q(\mathrm{gr}^p \barB(\cA))$ \\[2pt]
Convergence radius &
Koszul locus: $E_2$~degeneration
(Theorem~\ref{thm:spectral-sequence-collapse}) \\[2pt]
Analytic continuation past radius &
Coderived category completion
(\S\ref{subsec:chiral-coderived-contraderived}) \\[2pt]
$\log(ab) = \log(a) + \log(b)$ &
$Q_g(\cA) + Q_g(\cA^!) = H^*(\overline{\mathcal{M}}_g, Z_\cA)$
(Theorem~\ref{thm:quantum-complementarity-main}) \\[2pt]
Single-valued on simply connected domain &
$\dzero^2 = 0$ at genus~$0$
(Theorem~\ref{thm:bar-nilpotency-complete}) \\[2pt]
Multi-valued on $\mathbb{C}^\times$; monodromy $2\pi i$ &
$\dfib^{\,2} = \kappa(\cA) \cdot \omega_g$ at genus~$g \geq 1$ \\[2pt]
Residue at branch point &
Curvature $\kappa(\cA)$ \\[2pt]
Leading coefficient of $\log(1+z) = z + \cdots$ &
Modular characteristic $\kappa(\cA)$
(Theorem~\ref{thm:modular-characteristic})
\end{tabular}
\end{center}

\begin{remark}[The logarithmic kernel]
\label{rem:logarithmic-kernel}
\index{logarithmic kernel}
The fact that the bar construction uses a \emph{logarithmic} kernel
$\eta_{ij} = d\log(z_i - z_j)$ is the surface manifestation of the
categorical identification.  The classical logarithm of a product is a
sum: $\log(z_1 z_2) = \log z_1 + \log z_2$.  The bar differential
implements precisely this: the OPE (a product structure at colliding
points) is converted, via the residue $\mathrm{Res}_{z_i = z_j}
(\mu^{\mathrm{ch}} \cdot \eta_{ij})$, into a sum (the bar
differential is a sum over pairwise collisions).  The kernel $\eta$ is
the infinitesimal version of this conversion.
\end{remark}

\subsection{The Taylor expansion of the logarithm}
\label{subsec:taylor-expansion-log}
\index{PBW spectral sequence!as Taylor expansion}

The PBW spectral sequence of a chiral algebra~$\cA$
(Definition~\ref{def:chiral-koszul-pair}) is the Taylor expansion of
the categorical logarithm.

More precisely: the weight filtration on the bar complex
$\barB(\cA) = \bigoplus_{n \geq 0} (s^{-1}\overline{\cA})^{\otimes n}$
induces a spectral sequence
\[
E_1^{p,q} \;=\; H^q\bigl(\mathrm{gr}^p\, \barB(\cA)\bigr)
\;\Longrightarrow\;
H^{p+q}(\barB(\cA))\,.
\]
In the exp/log framework, the filtration degree~$p$ is the
\emph{order of the Taylor expansion}: the $p$-th filtered piece
$F^p\barB(\cA)$ retains contributions from at most $p$~points in
configuration space, i.e., the first $p$~terms of the logarithmic
series.  The differential $d_1$ on the $E_1$-page extracts the
\emph{leading term} of the logarithm (the binary OPE residue); higher
differentials $d_r$ capture \emph{higher-order corrections} from
$r$-fold collisions.

\begin{proposition}[Convergence criterion; \ClaimStatusProvedElsewhere{}
Theorems~\ref{thm:spectral-sequence-collapse}
and~\ref{thm:bar-cobar-inversion-qi}]
\label{prop:log-convergence}
\index{convergence!of categorical logarithm}
The categorical logarithm \emph{converges}---meaning $\exp \circ \log
= \mathrm{id}$---if and only if the PBW spectral sequence degenerates
at~$E_2$.  The $E_2$~degeneration is equivalent to:
\begin{enumerate}[label=(\roman*)]
\item The chiral algebra~$\cA$ lies on the \emph{Koszul locus}
(Definition~\ref{def:chiral-koszul-pair});
\item The Taylor expansion has finitely many nonzero corrections at
each filtration degree: the logarithm is ``polynomial'' in the
filtration variable;
\item The counit $\psi \colon \Omega\barB(\cA) \to \cA$ is a
quasi-isomorphism
(Theorem~\ref{thm:bar-cobar-inversion-qi}).
\end{enumerate}
Off the Koszul locus, the Taylor series diverges in the ordinary
derived category.  The coderived category
(\S\ref{subsec:chiral-coderived-contraderived}) provides the analytic
continuation: it is the completion of the derived category that makes
the divergent logarithm well-defined, exactly as the maximal analytic
continuation of $\log z$ requires passage from $\mathbb{C}^\times$ to its
universal cover.
\end{proposition}

\begin{remark}[Convergence radius from OPE data]
\label{rem:convergence-radius-ope}
\index{convergence!radius from OPE poles}
\index{Koszul locus!characterization via OPE}
The analogy with power series provides a heuristic for the following
conjectural expectation: the convergence radius of the categorical
logarithm should be computable from the input data.
For the classical logarithm $\log(1+z) = \sum (-1)^{n+1} z^n/n$, the
radius is determined by the growth rate of the coefficients.  For the
categorical logarithm, the ``coefficients'' are the OPE residues, and
the ``growth rate'' is the complexity of multi-point collisions.

In concrete terms: Kac--Moody algebras have first-order OPE poles
(linear growth), and the categorical logarithm converges
(Theorem~\ref{thm:master-pbw}).  The Virasoro algebra has a
second-order pole from the central term, but the Sugawara constraint
tames the growth, and convergence holds
(Theorem~\ref{thm:virasoro-chiral-koszul}).  For non-Koszul algebras
(e.g., admissible-level affine algebras), the OPE singularity structure
generates higher differentials in the spectral sequence---the Taylor
coefficients grow too fast for convergence.  A precise bound relating
the OPE pole orders to the convergence radius of the categorical
logarithm is a natural target for future work.
\end{remark}

\subsection{Additivity and the branch structure}
\label{subsec:additivity-branch}
\index{categorical logarithm!additivity}
\index{complementarity!as additivity of logarithm}

The fundamental property of any logarithm is that it converts products
to sums.  For the categorical logarithm, this is the content of the
complementarity theorem.

\begin{proposition}[Additivity of the categorical logarithm;
\ClaimStatusProvedElsewhere{} Theorem~\ref{thm:quantum-complementarity-main}]
\label{prop:log-additivity}
Let $(\cA, \cA^!)$ be a Koszul pair.  The quantum corrections to the
bar complex satisfy
\[
Q_g(\cA) \;+\; Q_g(\cA^!)
\;=\; H^*(\overline{\mathcal{M}}_g,\, Z_\cA)\,.
\]
In the exp/log framework, this is the statement
$\log^{\mathrm{cat}}(\cA \otimes \cA^!) =
\log^{\mathrm{cat}}(\cA) + \log^{\mathrm{cat}}(\cA^!)$: the
logarithm of the Koszul product is the sum of the logarithms, and
the right-hand side is the total logarithmic data
$\log^{\mathrm{cat}}(\cA \otimes \cA^!)$ computed from the center~$Z_\cA$
via the Hodge cohomology of~$\overline{\mathcal{M}}_g$.

The Lagrangian decomposition
$C_g(\cA) = Q_g(\cA) \oplus Q_g(\cA^!)$ is the decomposition of the
total logarithm into its two \emph{branches}: the sheet associated
to~$\cA$ and the sheet associated to its Koszul dual.  The pairing
between them is the monodromy acquired when analytically continuing
from one branch to the other.
\end{proposition}

\begin{remark}[The categorical Baker--Campbell--Hausdorff formula]
\label{rem:categorical-bch}
\index{Baker--Campbell--Hausdorff formula!categorical analogue}
For the classical logarithm, $\log(e^X e^Y) = X + Y + \tfrac{1}{2}[X,Y] + \cdots$
(the BCH formula).  The categorical analogue is the twisted tensor
product decomposition: for an extension
$0 \to \cA' \to \cA \to \cA'' \to 0$ of chiral algebras, the bar
complex decomposes as
$\barB(\cA) \simeq \barB(\cA'') \otimes_\tau \barB(\cA')$,
where the twisting cochain~$\tau$ encodes the extension data through
iterated brackets, in direct analogy with the commutator corrections
of BCH\@.  This follows from the standard filtered bar construction
applied to the extension filtration, and the twisting cochain~$\tau$
can be computed order by order from the connecting maps of the
extension.  A systematic development of the categorical BCH, including
explicit formulas for the first correction terms and their geometric
content, is deferred to \S\ref{sec:maurer-cartan-curved}.
\end{remark}

\subsection{From single-valued to multi-valued: the genus transition}
\label{subsec:genus-transition-log}
\index{categorical logarithm!genus transition}
\index{monodromy!of categorical logarithm}

The deepest structural consequence of the exp/log identification is the
genus transition.

\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{p{5.5cm}p{5.5cm}}
\textbf{Classical complex analysis} & \textbf{Categorical logarithm} \\
\hline
Simply connected domain &
Genus~$0$: $\pi_1(C_2(\mathbb{P}^1)) = 0$ \\[2pt]
$\log$ is single-valued, holomorphic &
$\dzero^2 = 0$ (Arnold relations), no curvature \\[2pt]
Multiply connected domain ($\mathbb{C}^\times$) &
Genus~$g \geq 1$: $\pi_1(\Sigma_g) \neq 0$ \\[2pt]
$\log$ acquires monodromy $2\pi i n$ &
$\dfib^{\,2} = \kappa(\cA) \cdot \omega_g$ \\[2pt]
Residue at branch point: $\mathrm{Res}_{z=0}(dz/z) = 1$ &
Curvature: $\kappa(\cA) \in H^1(X, \cA) \otimes H^0(\overline{\mathcal{M}}_g, \omega)$ \\[2pt]
Total differential $d\log z$ is exact on universal cover &
Total differential $\Dg{g}^2 = 0$ after Gauss--Manin correction \\[2pt]
Period matrix $\tau_{ij} = \oint_{B_j} \omega_i$ &
Modular package $(\kappa, \Delta, \Theta, \Pi)$ \\[2pt]
Torelli: $\tau$ determines the curve &
Categorical Torelli: monodromy of $\barB_g$ determines~$\cA$
up to quasi-isomorphism (via Theorem~\ref{thm:bar-cobar-inversion-qi})
\end{tabular}
\end{center}

\begin{remark}[The chiral Riemann--Hilbert correspondence, revisited]
\label{rem:chiral-rh-revisited}
\index{Riemann--Hilbert correspondence!chiral}
The Riemann--Hilbert correspondence identifies flat connections
(nilpotent data: $\nabla^2 = 0$) with monodromy representations
(periodic data: $\rho(\gamma^N) = 1$ for finite-order monodromy).
The categorical logarithm instantiates this at the level of
factorization algebras:
\begin{enumerate}[label=(\roman*)]
\item The \emph{flat connection} is the total corrected differential
$\Dg{g}$ with $\Dg{g}^2 = 0$, a flat connection on the bar family
$\barB_g(\cA) \to \overline{\mathcal{M}}_g$.
\item The \emph{curvature} of the fiberwise differential
$\dfib^{\,2} = \kappa \cdot \omega_g$ is the infinitesimal generator
of the monodromy.
\item The \emph{monodromy representation} is the action of the mapping
class group $\Gamma_g$ on $H^*(\barB_g(\cA))$, whose leading
eigenvalues are $\exp(2\pi i \kappa(\cA))$.
\end{enumerate}
The three differentials $\dzero$, $\dfib$, $\Dg{g}$
(Convention~\ref{conv:higher-genus-differentials}) are three levels of
the logarithm: the germ ($\dzero$, single-valued), the
multi-valued lift ($\dfib$, curvature $= $ residue), and the
trivialization on the universal cover ($\Dg{g}$, flat).
\end{remark}

\subsection{The characteristic hierarchy as logarithmic data}
\label{subsec:characteristic-log}
\index{modular characteristic!as logarithmic data}

The modular package $(\kappa, \Delta, \Theta, \Pi)$ of a chiral
algebra is the data of the categorical logarithm, organized by order:

\begin{enumerate}[label=\textbf{Level \arabic*}:, leftmargin=3.5em]
\item \textbf{Scalar logarithmic data.}  The modular
characteristic $\kappa(\cA)$ is the leading coefficient of the
categorical logarithm---the residue of the curvature.  Its
exponential is the scalar period~$N$: the smallest integer for which
$\exp(2\pi i N c/24) = 1$.  This is the content of Theorem~D
(Theorem~\ref{thm:modular-characteristic}).

\item \textbf{Spectral logarithmic data.}  The spectral
discriminant~$\Delta(\cA)$ encodes the eigenvalues of the monodromy of
the categorical logarithm.  Its exponential is the periodicity
profile~$\Pi(\cA)$: the collection of periods of individual T-matrix
eigenvalues $\lambda_i = \exp(2\pi i(h_i - c/24))$.

\item \textbf{Full logarithmic data.}  The universal Maurer--Cartan
class $\Theta_\cA \in H^2(\overline{\mathcal{M}}_g, Z_\cA)$
(Theorem~\ref{thm:mc2-full-resolution}) is the complete categorical
logarithm: it encodes all genus-$g$ corrections to the bar
differential.  Its exponential is the full modular automorphy of~$\cA$:
the action of $\Gamma_g$ on the conformal blocks, i.e., the modular
functor.
\end{enumerate}

\noindent
The hierarchy is controlled by a single principle: \emph{each level is
the leading term of the next}.  The scalar characteristic~$\kappa$ is
the trace of the spectral data~$\Delta$; the spectral data is the
eigenvalue decomposition of the full data~$\Theta$.  In the language of
complex analysis: $\kappa$ is the winding number of the logarithm,
$\Delta$ is the set of periods, and $\Theta$ is the full multi-valued
function.

\subsection{Visible theorems}
\label{subsec:visible-theorems-log}
\index{categorical logarithm!predicted theorems}

The exp/log identification makes certain results visible that would
otherwise have no natural formulation:

\begin{enumerate}[label=(\arabic*)]
\item \textbf{Categorical Torelli.}  If the monodromy of the
categorical logarithm (the higher-genus corrections to the bar
differential, encoded in~$\Theta_\cA$) determines~$\cA$ up to
quasi-isomorphism, this is a \emph{categorical Torelli theorem}.  It
follows from bar-cobar inversion (Theorem~\ref{thm:bar-cobar-inversion-qi})
plus the fact that the curvature determines the flat connection up to
gauge equivalence on a simply connected base: since the Teichm\"uller
space is contractible, the flat bar family is determined by its
curvature, i.e., by~$\kappa(\cA)$.

\item \textbf{Functional equation.}  The complementarity theorem
(Theorem~\ref{thm:quantum-complementarity-main}) is the \emph{functional equation} of the categorical
logarithm: it relates $\log^{\mathrm{cat}}(\cA)$ and
$\log^{\mathrm{cat}}(\cA^!)$ through the total data
$H^*(\overline{\mathcal{M}}_g, Z_\cA)$, exactly as the functional
equation of the Riemann $\zeta$-function relates $\zeta(s)$ and
$\zeta(1-s)$ through the $\Gamma$-factor.

\item \textbf{Acyclicity of the trivial algebra.}  For the unit
(trivial) chiral algebra $\cA = k$, the bar complex $\barB(k)$ is
acyclic: $H^*(\barB(k)) = k$ concentrated in degree~$0$.  In the
exp/log framework this is $\log(1) = 0$: the logarithm of the
multiplicative identity is the additive identity.

\item \textbf{Convergence radius from OPE poles.}  The Koszul locus
should be characterized by the singularity structure of the OPE: the
convergence radius of the categorical logarithm equals the inverse of
the growth rate of multi-point OPE singularities, in analogy with the
Cauchy--Hadamard formula.

\item \textbf{Screening as infinitesimal generator.}  In the lattice
setting (Construction~\ref{constr:lattice:screening}), the screening charges $Q_i$
with $Q_i^2 = 0$ are the infinitesimal generators of the categorical
logarithm; the quantum group relations $e_i^N = 0$ at $\zeta =
e^{2\pi i/N}$ are their $N$-th powers; and the representation category
$\mathrm{Rep}(\mathfrak{u}_\zeta(\mathfrak{g}))$ carries the periodic
(exponential) structure.  The passage $Q^2 = 0 \to e^N = 0$ is
literally exponentiation: the root of unity
$\zeta = \exp(2\pi i/N)$ is the monodromy of the categorical
logarithm around the $N$-th root.
\end{enumerate}

\begin{conjecture}[Factorization finiteness criterion;
\ClaimStatusConjectured]\label{conj:factorization-finiteness-criterion}
\index{factorization bar-cobar!finiteness criterion}
\index{thick generation!bypassed by sectorwise finiteness}
Let $\cA$ be a chiral algebra whose bar complex
$\barB(\cA)$ admits a bigrading
$\barB^{p,q}(\cA)$ with $\dim \barB^{p,q} < \infty$ for all
$(p,q)$.  Suppose the associated spectral sequence
$E_r^{p,q} \Rightarrow H^{p+q}(\barB(\cA))$ satisfies:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{(Convergence)} $E_r^{p,q} = E_\infty^{p,q}$
  for each $(p,q)$ at some finite page~$r_0(p,q)$;
\item \textup{(Sub-exponential growth)} $\dim E_1^{0,p} < c^p$
  for every $c > 1$ and all sufficiently large~$p$.
\end{enumerate}
Then the factorization bar-cobar adjunction restricts to an
equivalence on the Koszul locus, and the factorization DK
equivalence holds for~$\cA$ without thick generation.

\emph{Instances.}
For lattice algebras, (i)--(ii) are satisfied by the
$\Lambda$-grading with $E_1$~degeneration
\textup{(}Theorem~\textup{\ref{thm:lattice:factorization-koszul})}.
For Yangians, the root weight/loop degree bigrading of
Proposition~\textup{\ref{prop:yangian-bar-loop-weight}} gives (i),
and (ii) is proved in
Proposition~\textup{\ref{prop:lqt-e1-subexponential-growth}}: the
growth rate is $\sim\exp(\pi\sqrt{rp/12})$, which is sub-exponential.
For $\mathcal{W}$-algebras, the DS filtration provides a candidate
bigrading whose (ii) would follow from Kac--Kazhdan character
estimates.
\end{conjecture}

\subsection{The monograph as construction of a categorical logarithm}
\label{subsec:monograph-as-log}
\index{categorical logarithm!monograph structure}

Taken at full depth, the four main theorems are the four fundamental
properties of \emph{any} logarithm:
\begin{itemize}
\item \textbf{Theorem~A} (existence): the categorical logarithm and
exponential exist, as a pair of adjoint functors between augmented
factorization algebras and conilpotent factorization coalgebras.
\item \textbf{Theorem~B} (invertibility): on the convergence domain
(the Koszul locus), $\exp \circ \log = \mathrm{id}$, and the
logarithm faithfully encodes its input.
\item \textbf{Theorem~C} (branch structure): the failure of
convergence off the Koszul locus decomposes into complementary
Lagrangians---the two branches of the multi-valued logarithm---and the
total logarithmic data is the sum of the two branches.
\item \textbf{Theorem~D} (leading coefficient): the leading
coefficient $\kappa(\cA)$ of the logarithmic expansion determines the
full scalar package, just as the leading coefficient of
$\log(1+z) = z + \cdots$ determines the local behavior.
\end{itemize}

Every open problem in the monograph is a question about this
logarithm.  The five master conjectures are five aspects of one
question: \emph{what is the categorical logarithm for factorization
algebras on algebraic curves, completely?}
\begin{itemize}
\item \textbf{MC1}: does the logarithm converge? (PBW concentration)
\item \textbf{MC3}: what is the convergence domain? (thick generation
in category~$\mathcal{O}$)
\item \textbf{MC4}: does the logarithm extend to infinite rank?
(stability of towers)
\item \textbf{MC5}: does the physical logarithm (BRST) equal the
mathematical one (bar)? (BV--BRST identification)
\item \textbf{Periodicity}: what is the monodromy group of the
categorical logarithm?
\end{itemize}
These are not five separate programmes.  They are five windows onto a
single object.

\subsection{From tree-level to modular homotopy theory}
\label{subsec:tree-to-modular}
\index{modular homotopy theory!three-level ladder}

The constructions of this chapter are \emph{tree-level}: the bar
differential is indexed by collisions on a single smooth curve, and
the operadic compositions are indexed by planar rooted trees.  Three
levels of homotopy-algebraic structure emerge as one opens the genus
filtration.

\begin{definition}[Tree-level operadic homotopy theory]
\label{def:tree-level-homotopy}
A \emph{tree-level operadic homotopy theory} for a cyclic operad~$P$
is an $\infty$-category~$\mathcal{H}$ with homotopy-coherent
$P$-action: operations $m_T$ indexed by $P$-decorated rooted
trees~$T$, satisfying the operadic master equation $\sum_T m_T = 0$
up to coherent homotopies.  The bar-cobar constructions of this
chapter produce such a theory for $P = \chirCom$ or $P = \chirAss$.
\end{definition}

\begin{definition}[Modular homotopy theory, abstract]
\label{def:modular-homotopy-abstract}
A \emph{modular homotopy theory} for a modular operad~$M$ is an
$\infty$-category~$\mathcal{H}$ with homotopy-coherent $M$-action:
operations $m_\Gamma$ indexed by $M$-decorated \emph{stable
graphs}~$\Gamma$ (graphs with genus labels $g_v$ at each vertex,
satisfying $\sum_v g_v + b_1(\Gamma) = g$), compatible with
separating and nonseparating clutching
(Definition~\ref{def:modular-homotopy-theory-intro}).
\end{definition}

\begin{remark}[The formal step is small; the existence problem is hard]
\label{rem:trees-to-graphs}
Replacing rooted trees by stable graphs is the
\emph{only} combinatorial change from tree-level to modular homotopy
theory.  The formal generalization is immediate.  What is not
immediate is \emph{existence}: constructing the operations $m_\Gamma$
for graphs with loops requires integration over
$\overline{\mathcal{M}}_{g,n}$, which produces curvature
($\dfib^{\,2} \neq 0$) and demands the full Maurer--Cartan package
$\Theta_\cA$.  This is the content of
Chapter~\ref{chap:higher-genus}.
\end{remark}

\medskip

In Chapter~\ref{chap:higher-genus}, the curve itself varies over
$\overline{\mathcal{M}}_g$, and the bar differential acquires
curvature: the genus-$g$ correction $m_0^{(g)}$ is a section of the
obstruction sheaf on $\overline{\mathcal{M}}_g$, controlled by a
single universal Maurer--Cartan class $\Theta_{\cA}$.  The passage
from this chapter to the next is the passage from operadic to
\emph{modular} Koszul duality --- from the combinatorics of
associahedra to the geometry of the Deligne--Mumford
compactification --- or, in the language of the categorical logarithm,
the passage from the single-valued to the multi-valued regime.
