\chapter{The geometric bar complex}
\label{chap:bar-cobar}
\label{chap:bar-construction}


\index{bar construction!as integral transform|textbf}
\index{non-abelian Fourier transform|textbf}

Chapter~\ref{ch:algebraic-foundations} constructed the bar complex
over a point: a sum over sequences, with $d^2 = 0$ by
associativity.  This chapter constructs the bar complex over a
curve: a sum over configuration-space residues, with $d^2 = 0$ by
the Arnold relation.  The passage from sequences to residues is the
passage from algebra to geometry.

The bar complex replaces the multiplicative OPE of a chiral algebra with a nilpotent differential: it is the categorical logarithm.  Concretely, it is an integral transform over Fulton--MacPherson compactifications of configuration spaces, whose kernel is the logarithmic 1-form $\eta_{ij} = d\log(z_i - z_j)$ of \S\ref{sec:the-seed}.  The output is a factorization coalgebra $\barB(\cA)$ on $\operatorname{Ran}(X)$ with $d^2 = 0$ at genus~$0$.  Verdier duality inverts the transform: $\Omega \circ \barB \xrightarrow{\sim} \mathrm{id}$ on the Koszul locus (Theorem~\ref{thm:bar-cobar-inversion-qi}), recovering the algebra from its nilpotent image, the categorical exponential inverse to the logarithm (Remark~\ref{rem:nilpotence-periodicity}).

The three-step bar differential
$d = d_{\mathrm{internal}} + d_{\mathrm{residue}}
+ d_{\mathrm{de\,Rham}}$ that we built by hand for the Heisenberg
algebra in Chapter~\ref{ch:heisenberg-frame} now receives its general
formulation.  The three components
correspond to three types of geometry on the compactified
configuration space $\overline{C}_n(X)$:
\begin{center}
\small
\begin{tabular}{lll}
\textbf{Component} & \textbf{Geometric origin} & \textbf{Extracts} \\
\hline
$d_{\mathrm{internal}}$ & Internal differential of $\cA$ & Algebraic structure \\
$d_{\mathrm{residue}}$ & Residues along collision divisors $D_{ij}$ & OPE coefficients \\
$d_{\mathrm{de\,Rham}}$ & de~Rham differential on $\overline{C}_n(X)$ & Configuration geometry
\end{tabular}
\end{center}

\noindent
The Arnold relation
(Theorem~\ref{thm:arnold-three}) ensures $d^2 = 0$: it is the
coherence condition that the geometry of collisions is consistent.
The genus-$0$ bar differential $\dzero$ satisfies $\dzero^2 = 0$
(Theorem~\ref{thm:bar-nilpotency-complete}), and Verdier duality
establishes $\mathbb{D}_{\operatorname{Ran}} \barB_X(\cA) \simeq
\barB_X(\cA^!)$.  The curved genus-$g$ deformation, where the seed is
transplanted to higher-genus curves and curvature from the Hodge
bundle enters, is developed in Chapter~\ref{chap:higher-genus}.

\smallskip
\noindent\textit{Notation.}
Throughout this chapter, the unadorned differential $d$ on the bar complex denotes the genus-$0$ collision differential $\dzero$ of Convention~\ref{conv:higher-genus-differentials}; it satisfies $\dzero^2 = 0$ (Theorem~\ref{thm:bar-nilpotency-complete}).  The fiberwise curved differential $\dfib$ and the total corrected differential $\Dg{g}$ appear only in Chapter~\ref{chap:higher-genus}.

\medskip

\begin{convention}[Set notation and ordering]\label{conv:set-notation}
Throughout this chapter: collision divisors are $D_{ij}$ with $i < j$ (indices in increasing order); the hat notation $\widehat{ij}$ denotes \emph{omission} of both factors $\phi_i$ and $\phi_j$ after applying the OPE (we write $\widehat{ij}$ for the collision pattern itself, and $\widehat{\phi_i, \phi_j}$ when listing omitted terms in a tensor product).
\end{convention}

\begin{convention}[Bar coalgebra and Koszul dual algebra]
\label{conv:bar-coalgebra-identity}
\index{bar construction!as Koszul dual coalgebra|textbf}
\index{Koszul dual!coalgebra vs.\ algebra|textbf}
The bar construction $\barB_X(\cA)$ of an augmented chiral
algebra~$\cA$ is a dg factorization \emph{coalgebra} on
$\operatorname{Ran}(X)$.  It is the Koszul dual \emph{coalgebra}
of~$\cA$: the bar complex is not a tool for computing the dual,
it \emph{is} the dual.

When $\cA$ is Koszul, the bar coalgebra has cohomology concentrated
in bar degree~$1$.  The Koszul dual \emph{algebra}~$\cA^!$ is a
separate object: it has generators $\mathcal{V}^\vee =
\mathcal{H}om_{\mathcal{O}_X}(\mathcal{V}, \omega_X)$
($\mathcal{D}_X$-module dual of the generators of~$\cA$) and
relations~$R^\perp$ (orthogonal complement under the residue
pairing).  In the classical setting (algebras on a point),
$\cA^!$ is the graded linear dual of the concentrated bar
coalgebra.  In the chiral setting, $\cA^!$ is characterized by
Theorem~A (Theorem~\ref{thm:bar-cobar-isomorphism-main}):
Verdier duality on $\operatorname{Ran}(X)$ intertwines the bar
\emph{coalgebras},
\[
\mathbb{D}_{\operatorname{Ran}}\, \barB_X(\cA)
\;\simeq\; \barB_X(\cA^!),
\]
and the cobar--bar counit
$\Omega_X(\barB_X(\cA)) \xrightarrow{\sim} \cA$
(Theorem~\ref{thm:bar-cobar-inversion-qi})
is a \emph{resolution} of~$\cA$: the cobar of the bar coalgebra
recovers~$\cA$ itself, not its dual.

The bar-dual identity has a precise witness: the \emph{canonical
twisting morphism}
$\tau \colon \barB_X(\cA) \to \cA$,
the degree-$+1$ map projecting bar generators to their algebra
images.  The graded vector space
$\mathfrak{g}_\tau := \Hom(\barB_X(\cA),\, \cA)$ carries a
natural dg Lie structure, the \emph{convolution Lie algebra}, whose
bracket is $[f, g] = \mu_\cA \circ (f \otimes g) \circ
\Delta_{\barB}$ and whose differential is
$\partial f = d_\cA \circ f - (-1)^{|f|} f \circ d_{\barB}$.
(This dg~Lie algebra is the truncation of a full $L_\infty$-structure
arising from the operadic convolution; the higher brackets
$\ell_n$ for $n \ge 3$ encode homotopy-transfer data and are
recovered via graph sums, see
Theorem~\ref{thm:modular-quantum-linfty}.)
The twisting morphism~$\tau$ is a \emph{Maurer--Cartan element}
of this Lie algebra:
\[
\partial\tau + \tfrac{1}{2}[\tau, \tau] = 0
\qquad
\bigl(\text{equivalently: } \partial\tau + \tau \star \tau = 0\bigr),
\]
and the bar-cobar adjunction is the pair
$(\varepsilon_\tau,\, \eta_\tau)$ it determines.
At higher genus, $\tau$ extends to a curved MC element
$\tau_{\mathrm{mod}} = \tau + \Theta_\cA$
in the modular convolution algebra
$\mathfrak{g}_\tau \widehat{\otimes} R\Gamma(\overline{\mathcal{M}}_{g,\bullet})$
(Remark~\ref{rem:theta-modular-twisting}), whose curvature
$\kappa(\cA)\cdot\omega_g$ controls the genus tower.
The four main theorems are four properties of~$\tau$:
existence~(A), invertibility~(B), branch structure~(C),
leading coefficient~(D).

\smallskip\noindent
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lll}
\textbf{Object} & \textbf{Type} & \textbf{Relationship} \\
\hline
$\barB_X(\cA)$ & factorization coalgebra
  & the Koszul dual coalgebra \\[2pt]
$\cA^!$ & chiral algebra
  & generators $= \mathcal{V}^\vee$,
    relations $= R^\perp$ \\[2pt]
$\mathbb{D}_{\operatorname{Ran}}\barB_X(\cA)$
  & factorization coalgebra
  & $\simeq \barB_X(\cA^!)$ (Theorem~A) \\[2pt]
$\Omega_X(\barB_X(\cA))$ & chiral algebra
  & $\simeq \cA$ (resolution, not $\cA^!$)
\end{tabular}
\end{center}
\end{convention}

\begin{convention}[Chiral product vs.\ chiral bracket]
\label{conv:product-vs-bracket}
\index{chiral product|textbf}
\index{chiral bracket|textbf}
The \emph{chiral product}
$\mu \colon j_* j^*(\cA \boxtimes \cA) \to \Delta_!(\cA)$
(Definition~\ref{def:chiral-algebra}) encodes all OPE pole
orders simultaneously.  The \emph{chiral bracket}
$\{a,b\} = a_{(0)}b$ extracts the simple-pole residue of~$\mu$;
the \emph{invariant pairing} $\kappa(a,b) = a_{(1)}b$ extracts
the double-pole residue.  The bar differential
$d_{\mathrm{res}}$ uses the full product~$\mu$
(Proposition~\ref{prop:pole-decomposition}), which decomposes as
$d_{\mathrm{res}} = d_{\mathrm{bracket}} + d_{\mathrm{curvature}}$:
the bracket component uses $\{,\}$; the curvature component
uses~$\kappa$.  Neither component is individually a differential
(\S\ref{sec:selection-principle}).
\end{convention}

\section{The geometric bar complex}
\label{sec:bar-cobar}

\subsection{OPE coefficients as residues}

\begin{remark}[Physical origin]\label{rem:physical-genesis}
In 2D conformal field theory, the operator product expansion (OPE)
\[\phi_i(z)\phi_j(w) = \sum_{k} \frac{C_{ij}^k}{(z-w)^{h_i+h_j-h_k}} \phi_k(w) + \text{(less singular)}\]
encodes the structure constants $C_{ij}^k$ (fusion rules) and conformal weights $h_i$ of the theory; associativity of multiple OPEs constrains the $C_{ij}^k$.
The bar construction geometrizes this: $\overline{C}_n(X)$ parametrizes insertion points, $D_{ij}$ encodes the limit $z_i \to z_j$, $\eta_{ij} = d\log(z_i - z_j)$ carries the singularities, and $\operatorname{Res}_{D_{ij}}$ extracts the OPE coefficients.
\end{remark}

\begin{remark}[Parallel track: the BV complex]\label{rem:bv-parallel-track}
\index{BV complex!parallel track}
The bar complex developed in this chapter has a second life as the
BV complex of a chiral field theory.  In the BV formalism
(Costello--Gwilliam~\cite{CG17}), a chiral algebra~$\cA$ determines a
classical field theory whose fields are generators of~$\cA$ and whose
\emph{antifields} are cogenerators of~$\cA^!$; the BV bracket arises from
the residue pairing on configuration spaces.  The identification
\[
\text{bar complex of } \cA
\;=\; \text{BV complex of the chiral field theory of } \cA
\]
is made precise in Theorem~\ref{thm:brst-bar-genus0}.  The dictionary
is complete:

\begin{center}
\small
\begin{tabular}{ll}
\textbf{This chapter} & \textbf{BV reading} \\ \hline
Bar differential $d_{\mathrm{res}}$ & BRST operator \\
Logarithmic form $\eta_{ij}$ & Propagator \\
Arnold relation $\Rightarrow d^2 = 0$ & Quantum master equation \\
Bar cohomology $H^*(\bar{B}(\cA))$ & Physical observables \\
Curvature $m_0$ (Chapter~\ref{chap:higher-genus}) & Conformal anomaly
\end{tabular}
\end{center}
\noindent
This is not an analogy; it is Theorem~\ref{thm:brst-bar-genus0}.
The algebraic-geometric side comes first because it admits complete
proofs; the physical identifications are then theorems, not
heuristics.
\end{remark}

\begin{example}[OPE as residue: the Heisenberg current]\label{ex:ope-to-residue}
The Heisenberg current $J(z)$ with OPE $J(z)J(w) = k/(z-w)^2 + \text{reg.}$ gives the bar element $J(z_1) \otimes J(z_2) \otimes \eta_{12} \in \bar{B}^2(\mathcal{H})$, where $\eta_{12} = d\log(z_1 - z_2)$.  The bar differential extracts a residue: setting $\epsilon = z_1 - z_2$, the OPE double pole combined with $\eta_{12}$ produces $\operatorname{Res}_{\epsilon=0}[\epsilon^{-3}d\epsilon] = 0$ (triple pole, no residue).  The central charge $k$ is invisible at genus~$0$; it appears at genus~$1$ as the curvature $m_0$ (Example~\ref{ex:heisenberg-d-deg1}).
\end{example}

\begin{remark}[Logarithmic forms are forced]\label{rem:why-log-forced}
Logarithmic forms $\eta_{ij} = d\log(z_i - z_j)$ are distinguished among meromorphic 1-forms with poles along diagonals by three requirements, which together determine them uniquely.

\emph{Conformal invariance.}
Under a conformal transformation $z \mapsto f(z)$, a direct computation gives
$d\log(f(z_i) - f(z_j)) = \frac{f'(z_i)dz_i - f'(z_j)dz_j}{f(z_i) - f(z_j)}$,
which near the diagonal $z_i \approx z_j$ reduces to $(dz_i - dz_j)/(z_i - z_j)$
by cancellation of $f'$.  Thus $\eta_{ij}$ is conformally invariant up to regular terms.

\emph{Well-defined residues.}
The residue $\operatorname{Res}_{D_{ij}}$ requires a \emph{simple pole} along $D_{ij}$: forms with higher-order poles (e.g.\ $dz_i/(z_i - z_j)^2$) do not admit canonical residues.  A logarithmic form $\omega = \frac{df}{f} \wedge \alpha + \beta$ with $f = z_i - z_j$ has $\operatorname{Res}_{D_{ij}}(\omega) = \alpha|_{D_{ij}}$, which is canonical.

\emph{Arnold relations.}
The cyclic identity
$\eta_{ij} \wedge \eta_{jk} + \eta_{jk} \wedge \eta_{ki} + \eta_{ki} \wedge \eta_{ij} = 0$
is the form-level expression of $d^2 = 0$ on configuration spaces; it holds for $d\log$ forms and fails for other meromorphic 1-forms with simple poles.

Logarithmic forms are therefore the unique solution to the constraints of conformal invariance, canonical residues, and differential nilpotence.
\end{remark}

\subsection{Non-abelian Poincaré perspective on bar construction}

\begin{definition}[Bar as factorization homology]\label{def:bar-fh}
The geometric bar construction is factorization homology of the
chiral algebra, following the Beilinson--Drinfeld factorization
framework~\cite[\S3.4]{BD04}:
\[\bar{B}^{\text{geom}}_n(\mathcal{A}) = \int_{\overline{C}_{n+1}(X)/X} \mathcal{A}\]
where we integrate over configuration spaces relative to $X$.
\end{definition}

\begin{remark}[Configuration spaces]\label{rem:why-config-NAP}
In non-abelian Poincar\'e duality~\cite[\S3.4]{BD04}, one integrates
over configuration spaces rather than the manifold itself.  The
compactification $\overline{C}_n(X)$ adds boundary divisors encoding
collision data; the key inputs are~\cite[Theorem~3.4.22, \S3.6]{BD04}
(Ran space as the correct geometric setting).  Residue extraction is
the NAP analogue of the cup product.
\end{remark}

\begin{theorem}[Bar construction as NAP homology; \ClaimStatusProvedHere]\label{thm:bar-NAP-homology}\label{thm:bar-computes-chiral-homology}
\index{factorization homology!via bar complex}
Let $\mathcal{A}$ be a chiral algebra on a smooth curve $X$ satisfying:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Holonomicity}: $\mathcal{A}$ is a holonomic
  $\mathcal{D}_X$-module (equivalently, locally finitely generated
  with regular singularities).  Concretely, the solution space of the
  $\mathcal{D}_X$-equations on any disk is finite-dimensional, the
  algebraic counterpart of finite-dimensional state spaces at each
  point.
\item \emph{Excision}: the factorization algebra associated
  to~$\mathcal{A}$ satisfies the Weiss cosheaf condition
  (Definition~\ref{def:weiss-cover}), i.e., the
  factorization structure glues over Weiss covers.  This
  provides the descent data for factorization homology.
\end{enumerate}
Then the geometric bar complex computes factorization homology:
\[H_*(\bar{B}^{\text{geom}}(\mathcal{A})) \cong \int_{C_*(X)} \mathcal{A}\]

This is factorization homology of $X$ with coefficients in $\mathcal{A}$ in the sense of Ayala--Francis~\cite{AF15}.  Holonomicity guarantees finite-dimensionality of stalks, which is needed for the Ayala--Francis identification~\cite[Theorem~5.1]{AF15}; excision provides the descent data.

The coalgebra structure on $\bar{B}^{\text{geom}}(\mathcal{A})$ arises from the coproduct in factorization homology:
\[\int_X A \to \int_{X_1} A \otimes \int_{X_2} A\]
when X decomposes as $X = X_1 \sqcup X_2$.
\end{theorem}

\begin{proof}
The identification follows from \cite{AF15} (for the factorization homology framework) and \cite{BD04} (Section~3.4, for the chiral algebra case).  The bar differential $d = d_{\text{int}} + d_{\text{res}} + d_{dR}$ corresponds to the three components of the factorization structure:
\begin{itemize}
\item $d_{\text{int}}$: Internal operations in $\mathcal{A}$ (factorization algebra structure)
\item $d_{\text{res}}$: Residues at collisions (the chiral bracket, realizing the NAP cup product)
\item $d_{dR}$: de Rham differential on logarithmic forms
\end{itemize}
The key verification is that Weiss covers of $C_n(X)$ compute factorization homology (\cite{AF15}, Theorem~5.1), and the FM compactification provides a canonical system of Weiss covers whose \v{C}ech complex is precisely the bar complex (Definition~\ref{def:weiss-cover}).
\end{proof}

\begin{remark}[The nilpotence-periodicity correspondence]
\label{rem:nilpotence-periodicity}
\index{nilpotence-periodicity correspondence|textbf}
\index{periodicity!as exponential of nilpotence}
The logarithmic form~$\eta_{ij} = d\log(z_i - z_j)$ is not an
incidental choice of kernel: the bar construction is the
\emph{categorical logarithm} for chiral algebras, mapping
multiplicative structure (the OPE) to additive/nilpotent structure
(the bar differential with $\dzero^2 = 0$).  The cobar construction
is the corresponding \emph{exponential}, reconstructing the algebra
from the nilpotent data.  The structural principle governing the
entire theory is:
\begin{center}
\emph{Nilpotence is the logarithm of periodicity.}
\end{center}
At genus~$0$, the logarithm~$\eta_{ij}$ is single-valued
on~$C_2(\mathbb{P}^1)$, the bar differential is nilpotent
($\dzero^2 = 0$), and the monodromy is trivial.  At
genus~$g \geq 1$, the logarithm $d\log E(z_i,z_j)$ acquires
monodromy around the $B$-cycles of~$\Sigma_g$, the fiberwise bar
differential fails nilpotence by
$\dfib^{\,2} = \kappa(\cA)\cdot\omega_g$, and the curvature
$\kappa(\cA)$ is the \emph{infinitesimal generator} of this
monodromy: the residue at the branch point of the logarithm.
This is the chiral Riemann--Hilbert correspondence: the nilpotent
datum~$\kappa$ determines the periodic datum (the monodromy of the
bar family over~$\overline{\mathcal{M}}_g$) via exponentiation.

The four theorems are four aspects of this correspondence:
Theorem~A asserts that the categorical logarithm and exponential
exist; Theorem~B that they are mutually inverse on the
convergence domain (the Koszul locus); Theorem~C that the failure
off the convergence domain decomposes into complementary
Lagrangians (the branch structure of the logarithm); and
Theorem~D that the leading coefficient~$\kappa(\cA)$ of the
logarithm determines the full scalar package.

The modular periodicity profile~$\Pi(\cA)$ is the
global/exponential counterpart of the infinitesimal/nilpotent
characteristic~$\kappa(\cA)$.  At the scalar level, the T-matrix
eigenvalues $\lambda = \exp(2\pi i(h - c/24))$ are the
\emph{exponentials} of conformal weights shifted by the central
charge; the modular period~$N$ is the smallest positive integer for
which $\exp(2\pi i N c/24) = 1$.  At the geometric level, the
nilpotency $\kappa(\lambda)^{g-1} = 0$
(Theorem~\ref{thm:geometric-depth-smooth}) makes the operator
$\exp(\kappa(\lambda))$ \emph{unipotent}, not periodic: geometry
provides a stabilization threshold, not a period.  True periodicity
arises from modular and quantum sources whose nilpotent generators
have finite-order exponentials.
\end{remark}

\subsection{Precise construction of the bar complex}

\begin{definition}[Genus-graded geometric bar complex, preliminary form]
\label{def:geom-bar-preview}
The bar complex at genus $g$ and bar degree~$n$ is, in first
approximation:
\[\bar{B}^{(g),n}(\mathcal{A}) = \Gamma\left(\overline{C}_{n+1}^{(g)}(\Sigma_g), j_*j^*\mathcal{A}^{\boxtimes(n+1)} \otimes \Omega^n(\log D^{(g)})\right)\]
The total bar complex is
$\bar{B}(\mathcal{A}) = \bigoplus_{g \geq 0} \bar{B}^{(g)}(\mathcal{A})$.
The complete definition, incorporating the bigrading by bar
degree~$p$ and form degree~$q$ together with the genus-graded
orientation bundle $\mathrm{or}_{p+1}^{(g)}$, is given in
Definition~\ref{def:geom-bar} below.
\end{definition}

\begin{convention}[Global sections vs.\ derived global sections]\label{conv:gamma-vs-rgamma}
\index{global sections!underived vs.\ derived}
Throughout this chapter, $\Gamma(-)$ denotes \emph{underived} global sections:
for a sheaf $\mathcal{F}$ on a variety $Y$, the symbol $\Gamma(Y, \mathcal{F})$
is the vector space $H^0(Y, \mathcal{F})$.  When derived global sections are
needed (e.g., over moduli stacks or in derived $\mathcal{D}$-module arguments),
we write $R\Gamma$ explicitly.  In particular, the bar complex definition above
uses honest global sections of a coherent sheaf on the smooth variety
$\overline{C}_{n+1}^{(g)}(\Sigma_g)$.
\end{convention}

\begin{remark}[Components of the definition]\label{rem:unpacking-bar-def}
The FM compactification $\overline{C}_{n+1}^{(g)}(\Sigma_g)$ parametrizes $(n+1)$ points on $\Sigma_g$ with collision patterns (Chapter~\ref{chap:config-spaces}).  The degree-$n$ bar complex has $(n+1)$ insertions $\phi_0(z_0) \otimes \cdots \otimes \phi_n(z_n)$, where $\phi_0$ is the ``output'' (operadic structure).

The external tensor product $j_*j^*\mathcal{A}^{\boxtimes(n+1)}$ extends $\mathcal{A}^{\boxtimes(n+1)}$ from the open locus of distinct points across collisions, with the OPE controlling the singularity structure (BD~\cite[\S3.4.14--3.4.22]{BD04}).

The logarithmic forms $\Omega^n(\log D^{(g)})$ are spanned at genus~$0$ by wedge products of $\eta_{ij} = d\log(z_i - z_j)$; at genus $g \geq 1$, theta functions ($g=1$) and prime forms ($g \geq 2$) contribute.

A global section $\alpha \in \bar{B}^{(g),n}(\mathcal{A})$ is a ``correlation function'':
\[\alpha = \sum_I a_I(z_0, \ldots, z_n) \cdot \phi_{i_0}(z_0) \otimes \cdots \otimes \phi_{i_n}(z_n) \otimes \omega_I(z_0, \ldots, z_n)\]
the geometric incarnation of an $(n+1)$-point function.
\end{remark}

\begin{example}[Genus zero, degree 1]\label{ex:bar-genus0-deg1}
At genus 0, degree 1:
\[\bar{B}^{(0),1}(\mathcal{A}) = \Gamma\left(\overline{C}_2(\mathbb{P}^1), j_*j^*(\mathcal{A} \boxtimes \mathcal{A}) \otimes \Omega^1(\log D_{12})\right)\]

\emph{Configuration space.} $C_2(\mathbb{P}^1) \subset (\mathbb{P}^1)^2$ has $\dim_\mathbb{C} = 2$.  The $\text{PSL}_2$ action is transitive on ordered pairs of distinct points, so the quotient $C_2(\mathbb{P}^1)/\text{PSL}_2$ is a point.  After fixing the $\text{PSL}_2$ gauge (e.g., $z_2 = \infty$), the residual coordinate is $z_1 \in \mathbb{C}$.

\emph{Boundary divisor.} $D_{12} = \{z_1 = z_2\}$ is a single point in $\overline{C}_2(\mathbb{P}^1)$.

\emph{Logarithmic 1-forms.} $\Omega^1(\log D_{12})$ consists of forms:
\[\omega = f(z_1, z_2) \cdot \eta_{12}\]
where $\eta_{12} = \frac{dz_1 - dz_2}{z_1 - z_2}$ and $f$ is a meromorphic function.

\emph{Elements.} Typical element is:
\[\phi_i(z_1) \otimes \phi_j(z_2) \otimes \eta_{12}\]

\emph{Dimension.} If $\mathcal{A}$ has $N$ generators, then:
\[\dim \bar{B}^{(0),1}(\mathcal{A}) = N^2 \cdot \dim H^0(\overline{C}_2(\mathbb{P}^1), \Omega^1(\log D_{12}))\]

For $\mathbb{P}^1$, $\dim H^0(\overline{C}_2, \Omega^1(\log D)) = 1$ (only constant coefficient functions after fixing $\text{PSL}_2$).

Hence $\dim \bar{B}^{(0),1}(\mathcal{A}) = N^2$.
\end{example}

\begin{example}[Genus zero, degree 2]\label{ex:bar-genus0-deg2}
At genus 0, degree 2:
\[\bar{B}^{(0),2}(\mathcal{A}) = \Gamma\left(\overline{C}_3(\mathbb{P}^1), j_*j^*(\mathcal{A}^{\boxtimes 3}) \otimes \Omega^2(\log D)\right)\]

\emph{Configuration space.} $\overline{C}_3(\mathbb{P}^1)$ has $\dim_\mathbb{C} = 3$.  Fixing the $\text{PSL}_2$ gauge (e.g., $z_3 = 0, z_2 = 1, z_1 = \infty$ for the normalization), the quotient $\overline{C}_3(\mathbb{P}^1)/\text{PSL}_2 \cong \overline{\mathcal{M}}_{0,4} \cong \mathbb{P}^1$ has $\dim_\mathbb{C} = 1$.  The $\text{PSL}_2$-reduced configuration has one free cross-ratio parameter.

\emph{Boundary divisor.} $D = D_{12} \cup D_{23} \cup D_{13}$ (three divisors, one for each pair of points colliding).

\emph{Logarithmic 2-forms.} $\Omega^2(\log D)$ is spanned by:
\[\eta_{12} \wedge \eta_{23}, \quad \eta_{23} \wedge \eta_{31}, \quad \eta_{31} \wedge \eta_{12}\]
subject to Arnold relation:
\[\eta_{12} \wedge \eta_{23} + \eta_{23} \wedge \eta_{31} + \eta_{31} \wedge \eta_{12} = 0\]

So the space of 2-forms is 2-dimensional (three generators, one relation).

\emph{Elements.} Typical element is:
\[\sum_{i,j,k} c_{ijk} \cdot \phi_i(z_1) \otimes \phi_j(z_2) \otimes \phi_k(z_3) \otimes (\eta_{12} \wedge \eta_{23})\]

\emph{Dimension.} 
\[\dim \bar{B}^{(0),2}(\mathcal{A}) = N^3 \cdot 2\]

This grows rapidly with $n$.
\end{example}

\subsubsection{The bar differential}

\begin{definition}[Bar differential]\label{def:bar-differential-complete}%
\label{def:geometric-bar}\label{def:geometric-bar-definition}\label{def:bar-geometric}%
\label{def:bar-diff-detailed}\label{def:diff-total}%
\index{bar complex!differential|textbf}
The bar complex carries a bigrading
$\barB_{p,q}(\cA)$ by \emph{bar arity}~$p$ (number of
desuspended tensor factors minus one) and
\emph{form degree}~$q$.  The \emph{cohomological
degree} of a homogeneous element
$s^{-1}\phi_0 \otimes \cdots \otimes s^{-1}\phi_p
\otimes \omega \in \barB_{p,q}$ is
\begin{equation}\label{eq:bar-cohomological-degree}
n \;=\; \sum_{i=0}^{p}\bigl(|\phi_i| - 1\bigr) + q
\;=\; \Bigl(\sum_{i=0}^{p} |\phi_i|\Bigr) - (p+1) + q,
\end{equation}
where $|\phi_i|$ is the internal (algebra) cohomological
degree and $-1$ is the desuspension shift.  The total
differential $d = d_{\mathrm{internal}} +
d_{\mathrm{residue}} + d_{\mathrm{form}}$ has
$|d| = +1$, verified component by component:
\begin{itemize}
\item $d_{\mathrm{internal}}$ preserves $(p,q)$ and
  increases some $|\phi_i|$ by $1$: net $n \mapsto n+1$.
\item $d_{\mathrm{residue}}$ maps
  $\barB_{p,q} \to \barB_{p-1,q}$: bar arity
  decreases by $1$ (two factors merge via~$\mu$), form
  degree is unchanged (the Poincar\'e residue extracts a
  scalar, not a form), and the desuspension
  contribution changes by $-(p) - (-(p+1)) = +1$:
  net $n \mapsto n+1$.
\item $d_{\mathrm{form}}$ maps
  $\barB_{p,q} \to \barB_{p,q+1}$: form degree
  increases by $1$ via~$d_{\mathrm{dR}}$:
  net $n \mapsto n+1$.
\end{itemize}
\noindent
The three components are:
\[d = d_{\text{internal}} + d_{\text{residue}} + d_{\text{form}}\]

\emph{Component 1: Internal differential $d_{\text{internal}}$.}

If $\mathcal{A}$ has an internal differential $d_\mathcal{A}: \mathcal{A} \to \mathcal{A}$ (e.g., from a BRST complex or de Rham differential), we apply it to each tensor factor:
\[d_{\text{internal}}\left(\phi_0 \otimes \cdots \otimes \phi_n \otimes \omega\right) = \sum_{i=0}^n (-1)^{\epsilon_i} \left(\phi_0 \otimes \cdots \otimes d_\mathcal{A}(\phi_i) \otimes \cdots \otimes \phi_n \otimes \omega\right)\]
where $\epsilon_i$ is the Koszul sign:
\[\epsilon_i = \sum_{j=0}^{i-1} |\phi_j| + \sum_{j=0}^{i-1} 1 = \text{(total degree before } \phi_i\text{)}\]

\emph{Component 2: Residue differential $d_{\text{residue}}$.}

The main geometric operation extracts OPE coefficients via residues at collision divisors.
\[d_{\text{residue}}\left(\phi_0 \otimes \cdots \otimes \phi_n \otimes \omega\right) = \sum_{0 \leq i < j \leq n} (-1)^{\sigma_{ij}} \text{Res}_{D_{ij}}\left[\mu(\phi_i, \phi_j) \otimes \text{(other factors)} \otimes \omega\right]\]
where:
\begin{itemize}
\item $\mu: \mathcal{A} \otimes \mathcal{A} \to \mathcal{A}$ is the OPE (chiral product)
\item $D_{ij} \subset \overline{C}_{n+1}(\Sigma_g)$ is the divisor where $z_i = z_j$
\item $\text{Res}_{D_{ij}}$ is the residue along $D_{ij}$ (see \S\ref{sec:residue-calculus} below)
\item $\sigma_{ij}$ is a sign determined by:
  \begin{enumerate}
  \item Position of $i,j$ in the tensor product (Koszul sign)
  \item Orientation of $D_{ij}$ as boundary (geometric sign)
  \item Grading of fields $\phi_i, \phi_j$ (super sign)
  \end{enumerate}
\end{itemize}

The explicit formula for the sign is:
\[\sigma_{ij} = \left(\sum_{k=0}^{i-1} |\phi_k|\right) + \left(\sum_{k=i+1}^{j-1} |\phi_k|\right) + |\phi_i| + \epsilon_{\text{geom}}(D_{ij})\]
where $\epsilon_{\text{geom}}(D_{ij}) = 0$ or $1$ depending on orientation convention (see Convention \ref{conv:orientations-enhanced}).

\emph{Component 3: Form differential $d_{\text{form}}$.}

Apply the de Rham differential to the form component:
\[d_{\text{form}}\left(\phi_0 \otimes \cdots \otimes \phi_n \otimes \omega\right) = (-1)^{\sum_{i=0}^n |\phi_i|} \left(\phi_0 \otimes \cdots \otimes \phi_n \otimes d_{\text{dR}}(\omega)\right)\]
where $d_{\text{dR}}: \Omega^n \to \Omega^{n+1}$ is the de Rham differential on forms.

\end{definition}

\begin{lemma}[$d_{\mathrm{form}}$ preserves
  logarithmic forms]\label{lem:ddr-preserves-log}
The de~Rham differential restricts to a map
$d_{\mathrm{dR}} \colon
  \Omega^q_{\overline{C}_{p+1}}(\log D) \to
  \Omega^{q+1}_{\overline{C}_{p+1}}(\log D)$,
so $d_{\mathrm{form}}$ is well-defined on the bar
complex.
\end{lemma}

\begin{proof}
A logarithmic $q$-form on a smooth variety~$Y$ with
normal-crossings divisor~$D$ is a section of
$\Omega^q_Y(\log D) = \bigwedge^q \Omega^1_Y(\log D)$.
The sheaf $\Omega^1_Y(\log D)$ is locally free,
generated over~$\cO_Y$ by $dz_1/z_1, \ldots, dz_r/z_r,
dz_{r+1}, \ldots, dz_n$ where $D = \{z_1 \cdots z_r = 0\}$.
Since $d_{\mathrm{dR}}(f \cdot dz_i/z_i) = df \wedge
dz_i/z_i$ and $df$ is a section of~$\Omega^1_Y(\log D)$
(regular functions have logarithmic differentials), the
wedge product remains in
$\Omega^{q+1}_Y(\log D)$.  This applies with
$Y = \overline{C}_{p+1}(\Sigma_g)$ and
$D = \partial\overline{C}_{p+1}(\Sigma_g)$, which is
normal-crossings by the Fulton--MacPherson construction
(\cite[Theorem~2]{FM94}).
\end{proof}

\begin{remark}[Three components]\label{rem:three-components}
\index{boundary divisor!in bar differential}
Each component has a geometric source and a physical identity:
$d_{\text{internal}}$ is the BRST operator on~$\cA$;
$d_{\text{residue}}$ extracts OPE coefficients via residues
at collision divisors~$D_{ij}$;
$d_{\text{form}}$ is the de~Rham differential on configuration space,
enforcing Ward identities
(Lemma~\ref{lem:ddr-preserves-log}).

Nilpotency $d^2 = 0$ is \emph{not} automatic.  Of the nine cross-terms in
$(d_1 + d_2 + d_3)^2$, the critical one is
$d_{\text{residue}}^2 = 0$: this requires the full Borcherds
identity, not merely Jacobi
(Proposition~\ref{prop:pole-decomposition}).  The remaining
cross-terms vanish by Stokes
($\{d_{\text{form}}, d_{\text{residue}}\} = 0$) and the
derivation property.
\end{remark}

\begin{example}[Heisenberg degree-\texorpdfstring{$1$}{1} bar differential]\label{ex:heisenberg-d-deg1}
\label{ex:free-boson-d-deg1}
The Heisenberg algebra $\mathcal{H}_k$ with OPE $J(z)J(w) = k/(z-w)^2 + \text{regular}$ has
vanishing bar differential on $\alpha = J \otimes J \otimes \eta_{12} \in \bar{B}^1$: the OPE combined with $\eta_{12}$ produces a triple pole $\epsilon^{-3}\,d\epsilon$, whose residue is zero.  The element $\alpha$ is a non-trivial cocycle.  The level $k$ is invisible at genus $0$ and appears only as a genus-$1$ quantum correction.  See Chapter~\ref{ch:heisenberg-frame}, \S\ref{sec:frame-bar-deg1} for the full computation.
\end{example}

\begin{definition}[Orientation bundle across genera]
For the configuration space $C_{p+1}^{(g)}(\Sigma_g)$, the orientation bundle includes genus-dependent factors:

\[\text{or}_{p+1}^{(g)} = \det(TC_{p+1}^{(g)}(\Sigma_g)) \otimes \text{sgn}_{p+1} \otimes \mathcal{L}_g\]

where:
\begin{enumerate}
\item $\det(TC_{p+1}^{(g)}(\Sigma_g))$ is the top exterior power of the tangent bundle
\item $\text{sgn}_{p+1}$ is the sign representation of $S_{p+1}$
\item $\mathcal{L}_g$ encodes the genus-dependent orientation from the period matrix
\end{enumerate}

This ensures $d^2 = 0$ with consistent signs across all face maps, compatibility with $\mathfrak{S}_{p+1}$, correct genus-graded $A_\infty$ signs, and $\text{Sp}(2g, \mathbb{Z})$-covariance.
\end{definition}

\begin{remark}[Orientation convention]
We fix orientations at each genus by complexifying the orientation sheaf of the real blow-up $\widetilde{C}_{p+1}^{(g)}(\mathbb{R})$, tensoring with $\text{sgn}_{p+1}$ so that $\sigma^* \text{or}_{p+1}^{(g)} = \text{sign}(\sigma) \cdot \text{or}_{p+1}^{(g)}$ for $\sigma \in S_{p+1}$, and at genus $g \geq 1$ including the period matrix orientation $\mathcal{L}_g$.
\end{remark}

\subsection{Sign conventions}\label{sec:sign-conventions}

\begin{convention}[Enhanced sign system]\label{conv:orientations-enhanced}
The bar complex requires three types of sign conventions:

\emph{Type 1: Koszul signs (algebraic).}

The standard Koszul sign rule (Appendix~\ref{app:signs}, \S\ref{app:sign-conventions}; see also \S\ref{sec:sign-dictionary-complete}) applies with total degree $|\phi| + k$ for a field $\phi \in \mathcal{A}$ tensored with a form in $\Omega^k$.

\emph{Type 2: Orientation signs (geometric).}

Configuration spaces and their boundary divisors carry orientations:

\begin{enumerate}
\item \emph{Configuration space orientation:} $\overline{C}_{n+1}(\Sigma_g)$ is oriented via the complex structure:
\[\text{or}(\overline{C}_{n+1}) = dz_1 \wedge d\bar{z}_1 \wedge \cdots \wedge dz_n \wedge d\bar{z}_n\]
(after modding out by automorphisms; see \S\ref{sec:sign-conventions} below)

\item \emph{Divisor orientation:} Each boundary divisor $D_{ij}$ is oriented by the \emph{outward normal} convention:
\[\text{or}(D_{ij}) = d\epsilon_{ij} \wedge \text{or}(\text{tangent to } D_{ij})\]
where $\epsilon_{ij} = |z_i - z_j|$ points outward (into the interior).

\item \emph{Codimension-2 strata:} At intersections $D_{ij} \cap D_{jk} = D_{ijk}$:
\[\text{or}(D_{ijk}) = d\epsilon_{ij} \wedge d\epsilon_{jk} \wedge \text{or}(\text{tangent})\]

The key identity (Lemma~\ref{lem:orientation}, item~(3)):
\[\text{or}(D_{ijk})|_{D_{ij}} = -\text{or}(D_{ijk})|_{D_{jk}}\]
This sign difference ensures Stokes' theorem holds with correct cancellations.

\item \emph{Residue orientation:} When computing $\text{Res}_{D_{ij}}$, we use:
\[\text{Res}_{D_{ij}}\left(\frac{d\epsilon_{ij}}{\epsilon_{ij}} \wedge \alpha\right) = (+1) \cdot \alpha|_{D_{ij}}\]
(no extra sign for residue extraction)
\end{enumerate}

\emph{Type 3: Operadic signs.}

The bar complex has an operadic structure (composition of operations). When composing two operations, the sign arises from three sources: \emph{grafting trees} (reordering edges when attaching one tree to another), \emph{shuffle signs} (permuting tensor factors to bring colliding fields together), and the \emph{Koszul sign} (moving differential forms past fields).

The formula (for operads): if we compose operations of arity $m$ and $n$ at the $i$-th input:
\[\text{sign} = (-1)^{\epsilon}\]
where:
\[\epsilon = \sum_{j=1}^{i-1} |p_j| \cdot |q|\]
($|p_j|$ are degrees of inputs before position $i$, $|q|$ is degree of the composed operation)

\emph{Compatibility condition.}

These three types of signs must be compatible to ensure $d^2 = 0$. The key relations are:

\begin{enumerate}
\item \emph{Koszul-Orientation compatibility:}
\[\text{sign}_{\text{Koszul}}(\phi_i \leftrightarrow \phi_j) \cdot \text{sign}_{\text{orient}}(D_{ij} \leftrightarrow D_{ji}) = (-1)^{1}\]
(fields anticommute up to orientation sign)

\item \emph{Orientation-Residue compatibility:}
\[\text{Res}_{D_{ij}} \circ \text{Res}_{D_{jk}} + \text{Res}_{D_{jk}} \circ \text{Res}_{D_{ij}} = 0 \quad \text{(with correct signs)}\]
(residues anticommute at codimension-2 strata)

\item \emph{Koszul-Operadic compatibility:}
\[\text{sign}_{\text{Koszul}}(\text{reorder}) = \text{sign}_{\text{operadic}}(\text{compose})\]
(both give the same sign for the same operation)
\end{enumerate}

\end{convention}

\begin{lemma}[Sign compatibility; \ClaimStatusProvedHere]\label{lem:sign-compatibility}
The three types of signs (Koszul, orientation, operadic) are mutually compatible in the sense required for $d^2 = 0$.
\end{lemma}

\begin{proof}
We verify each compatibility relation:

\emph{Relation 1: Koszul-Orientation.}

Consider swapping two fields $\phi_i \otimes \phi_j \to \phi_j \otimes \phi_i$:
- Koszul sign: $(-1)^{|\phi_i| \cdot |\phi_j|}$
- This corresponds to swapping collision divisors $D_{ij} \leftrightarrow D_{ji}$
- Orientation sign: $\text{or}(D_{ji}) = -\text{or}(D_{ij})$ (from antisymmetry of differentials)

The product:
\[(-1)^{|\phi_i| \cdot |\phi_j|} \cdot (-1) = (-1)^{|\phi_i| \cdot |\phi_j| + 1}\]

For bosonic fields ($|\phi_i|, |\phi_j|$ even), this is $(-1)^{0+1} = -1$.
For fermionic fields ($|\phi_i|, |\phi_j|$ odd), this is $(-1)^{1+1} = +1$.

This yields the correct commutation and anticommutation relations for super-objects.

\emph{Relation 2: Orientation-Residue.}

At a codimension-2 stratum $D_{ijk} = D_{ij} \cap D_{jk}$:

Approach from $D_{ij}$ side:
\[\text{or}(D_{ijk})|_{D_{ij}} = d\epsilon_{jk} \wedge \text{or}(D_{ij})\]

Approach from $D_{jk}$ side:
\[\text{or}(D_{ijk})|_{D_{jk}} = d\epsilon_{ij} \wedge \text{or}(D_{jk})\]

By Lemma~\ref{lem:orientation}(3), these differ by a sign: $\text{or}(D_{ijk})|_{D_{ij}} = -\text{or}(D_{ijk})|_{D_{jk}}$.

Now compute double residue:
\begin{align*}
\text{Res}_{D_{ij}} \text{Res}_{D_{jk}}(\omega) + \text{Res}_{D_{jk}} \text{Res}_{D_{ij}}(\omega) &= \int_{D_{ijk}} \omega|_{D_{ijk}} \text{ (from }\text{or}(D_{ijk})|_{D_{ij}}\text{)} \\
&\quad + \int_{D_{ijk}} \omega|_{D_{ijk}} \text{ (from }\text{or}(D_{ijk})|_{D_{jk}}\text{)} \\
&= (+1) \int + (-1) \int = 0
\end{align*}

The orientations differ by exactly the sign needed for cancellation.

\emph{Relation 3: Koszul-Operadic.}

Consider composing two operations $\mu_1: V_1 \otimes V_2 \to W_1$ and $\mu_2: W_1 \otimes V_3 \to W_2$.

Koszul sign for moving $V_2$ past $W_1$:
\[(-1)^{|V_2| \cdot |W_1|}\]

Operadic sign for grafting:
\[(-1)^{\epsilon}\] where $\epsilon = |V_1| + |V_2|$ (degrees of inputs before the graft point)

These match when we account for the suspension in the bar construction ($W_1$ has degree shifted by 1).  More precisely, the sign convention on the desuspension $s^{-1}\bar{\mathcal{A}}$ is \emph{chosen} so that the Koszul and operadic signs are compatible; we now verify that this choice is consistent.

\emph{General case.}
Let $T$ be the rooted tree labeling the given bar element.  Each of
the three sign sources defines a parity character on $\operatorname{Aut}(T)$:
Koszul signs come from permuting tensor factors, orientation signs
come from permuting configuration-space coordinates, and operadic
signs come from grafting odd inputs through the operad composition.

The key identity is checked on an adjacent transposition of two inputs
$\phi_i,\phi_j$.  On the desuspension $s^{-1}\bar{\mathcal{A}}$, that
transposition contributes
\[
(-1)^{(|\phi_i|-1)(|\phi_j|-1)}
= (-1)^{|\phi_i||\phi_j|}
  (-1)^{|\phi_i|+|\phi_j|}
  (-1).
\]
The first factor is the Koszul sign, the second is the operadic sign,
and the last factor is the orientation sign from swapping the two
coordinates.  Hence the combined action on
$s^{-1}\bar{\mathcal{A}}$ already contains all three sign sources.

Because every tree automorphism is generated by adjacent
transpositions, compatibility for generators implies
\[
\epsilon_{\mathrm{Koszul}} \cdot
\epsilon_{\mathrm{orient}} \cdot
\epsilon_{\mathrm{operad}} = +1
\]
for every rooted tree~$T$.  The arity-$2$ computation above supplies
the base case, and induction on tree depth propagates the identity to
all graftings.
\end{proof}

\subsection{\texorpdfstring{Proof that $d^2 = 0$: nine-term verification}{Proof that d2 = 0: nine-term verification}}\label{sec:bar-nilpotency-nine-terms-complete}\label{sec:bar-nilpotency}

\begin{theorem}[Nilpotency of bar differential; \ClaimStatusProvedHere]\label{thm:bar-nilpotency-complete}
\index{bar differential!nilpotence}
\textup{[Regime: quadratic, genus-$0$
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

The differential $d = d_{\text{internal}} + d_{\text{residue}} + d_{\text{form}}$ on the bar complex satisfies:
\[d^2 = 0\]

More precisely, all nine cross-terms arising from $(d_1 + d_2 + d_3)^2$ cancel.
\end{theorem}

\begin{proof}
Write $d = d_1 + d_2 + d_3$ where $d_1 = d_{\text{int}}$ is the internal differential on $\mathcal{A}$, $d_2 = d_{\text{res}}$ extracts residues at collision divisors, and $d_3 = d_{\text{dR}}$ is the de Rham differential on forms. Expanding $(d_1 + d_2 + d_3)^2$, we obtain six terms (three diagonal and three anticommutators) which we verify separately.

\emph{Diagonal terms.} The identity $d_1^2 = 0$ holds because $d_\mathcal{A}^2 = 0$ on $\mathcal{A}$: diagonal terms vanish by hypothesis, and cross-terms (where $d_1$ hits two different tensor factors $\phi_i$ and $\phi_j$) cancel in pairs by the Koszul sign rule. The identity $d_3^2 = 0$ is the standard relation $d_{\text{dR}}^2 = 0$ for differential forms.

The identity $d_2^2 = 0$ is the most substantial. In the double sum
\[d_2^2 = \sum_{i<j}\sum_{k<\ell} (-1)^{\sigma_{ij} + \sigma_{k\ell}'}\, \text{Res}_{D_{k\ell}} \circ \text{Res}_{D_{ij}},\]
three cases arise according to how the index sets $\{i,j\}$ and $\{k,\ell\}$ overlap.

\emph{Case (i): Disjoint pairs} ($\{i,j\} \cap \{k,\ell\} = \emptyset$). The divisors $D_{ij}$ and $D_{k\ell}$ intersect transversally in $\partial\overline{C}_{n+1}(X)$. Since the divisors are disjoint (no shared indices), the residue operations themselves commute:
\[\text{Res}_{D_{ij}} \circ \text{Res}_{D_{k\ell}} = \text{Res}_{D_{k\ell}} \circ \text{Res}_{D_{ij}}.\]
The cancellation comes from the signed sum in $d_2$: the ordered pairs $(i,j),(k,\ell)$ and $(k,\ell),(i,j)$ contribute with opposite signs $(-1)^{\sigma_{ij}+\sigma_{k\ell}'}$ and $(-1)^{\sigma_{k\ell}+\sigma_{ij}'}$ (Lemma~\ref{lem:sign-compatibility}), and these signs differ by $(-1)$, so the two terms cancel.

\emph{Case (ii): One overlap} (say $j = k$).
This is the case that produced the Arnold relation in the
Heisenberg degree-$2$ computation
(\S\ref{sec:frame-bar-deg2}): three boundary strata meet at a
triple collision, and their contributions cancel cyclically.
We give the complete argument.

\smallskip
\emph{Step (a): Identify the codimension-$2$ locus.}
When $|\{i,j\}\cap\{k,\ell\}|=1$, say $j=k$, the
double residue $\text{Res}_{D_{j\ell}}\circ\text{Res}_{D_{ij}}$
approaches the locus $D_{ij\ell} \subset
\overline{C}_{n+1}(X)$ where all three points $z_i,z_j,z_\ell$
collide simultaneously.  In the FM compactification, $D_{ij\ell}$
is a smooth codimension-$2$ stratum obtained by blowing up the
triple diagonal.  Exactly three codimension-$1$ boundary
divisors contain $D_{ij\ell}$, corresponding to the three
ways of performing the triple collision in two stages:
\[
D_{ij}\cap D_{j\ell}, \qquad
D_{j\ell}\cap D_{i\ell}, \qquad
D_{i\ell}\cap D_{ij}.
\]
The first collapses $z_i\to z_j$ and then $z_j\to z_\ell$;
the second collapses $z_j\to z_\ell$ and then $z_i\to z_\ell$;
the third collapses $z_i\to z_\ell$ and then $z_j\to z_\ell$.

\smallskip
\emph{Step (b): Extract the three iterated-residue terms.}
Each codimension-$1$ stratum through $D_{ij\ell}$ contributes
one iterated residue to $d_2^2$.  The chiral product
$\mu$ determines the algebra element produced at each stage:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item \emph{First $D_{ij}$, then $D_{j\ell}$.}
  Collapsing $z_i\to z_j$ applies
  $\mu(\phi_i,\phi_j)$; collapsing the result with $z_\ell$
  applies $\mu(-,\phi_\ell)$.  This gives:
  \[
  \text{Res}_{D_{j\ell}}\circ\text{Res}_{D_{ij}}
    \bigl[\mu\bigl(\mu(\phi_i,\phi_j),\,\phi_\ell\bigr)
    \otimes\omega\bigr].
  \]
\item \emph{First $D_{j\ell}$, then $D_{ij}$.}
  Collapsing $z_j\to z_\ell$ applies
  $\mu(\phi_j,\phi_\ell)$; collapsing with $z_i$ applies
  $\mu(\phi_i,-)$.  This gives:
  \[
  \text{Res}_{D_{ij}}\circ\text{Res}_{D_{j\ell}}
    \bigl[\mu\bigl(\phi_i,\,\mu(\phi_j,\phi_\ell)\bigr)
    \otimes\omega\bigr].
  \]
\item \emph{First $D_{i\ell}$, then $D_{ij}$.}
  Collapsing $z_i\to z_\ell$ applies
  $\mu(\phi_i,\phi_\ell)$; collapsing the result with $z_j$
  applies $\mu(-,\phi_j)$.  This gives:
  \[
  \text{Res}_{D_{i\ell}}\circ\text{Res}_{D_{ij}}
    \bigl[\mu\bigl(\mu(\phi_i,\phi_\ell),\,\phi_j\bigr)
    \otimes\omega\bigr].
  \]
\end{enumerate}
These are the only terms in $d_2^2$ that access the
codimension-$2$ locus $D_{ij\ell}$.  (All other pairs in the
double sum either have disjoint indices or identical indices,
handled by Cases~(i) and~(iii).)  The total contribution of
Case~(ii) at the triple $\{i,j,\ell\}$ is thus:
\begin{equation}\label{eq:case-ii-cyclic-sum}
\sum_{\textup{cyclic}}
  \text{Res}_{D_{j\ell}}\circ\text{Res}_{D_{ij}}
  \bigl[\mu\bigl(\mu(\phi_i,\phi_j),\,\phi_\ell\bigr)
  \otimes\omega\bigr]
= 0,
\end{equation}
where the cyclic sum runs over the three terms~(1)--(3).

\smallskip
\emph{Step (c): The geometric origin --- boundary of boundary.}
The relation $\partial^2=0$ on the cellular chain complex of
$\overline{C}_{n+1}(X)$ (Lemma~\ref{lem:orientation}) implies
that the signed sum of the codimension-$2$ faces arising from
any codimension-$2$ stratum vanishes.  Applied to $D_{ij\ell}$:
the three codimension-$1$ strata $D_{ij}$, $D_{j\ell}$,
$D_{i\ell}$ each pair to give a codimension-$2$ face through
$D_{ij\ell}$, and the boundary-of-boundary relation
$\partial^2=0$ asserts that these three faces, with their
orientation signs, sum to zero.  Since each face carries the
corresponding iterated residue of
$\mu(\mu(\phi_?,\phi_?),\phi_?)\otimes\omega$, the relation
$\partial^2=0$ translates directly into the algebraic identity
\eqref{eq:case-ii-cyclic-sum}.

\smallskip
\emph{Step (d): Equivalence with the Borcherds identity.}
The vanishing~\eqref{eq:case-ii-cyclic-sum} is precisely
axiom~(ii) of Definition~\ref{def:chiral-algebra}: the
associativity of the chiral product $\mu$, i.e., the
Borcherds identity.  Crucially, this identity couples
\emph{all} OPE pole orders simultaneously --- unlike the
Jacobi identity, which governs only the simple-pole bracket
$\{-,-\} = (-)_{(0)}(-)$.
The Borcherds identity is both necessary and sufficient for the
vanishing: any meromorphic product $\mu$ satisfying
locality~(i) and producing $d_2^2=0$ must satisfy~(ii), and
conversely any chiral algebra (satisfying~(ii) by definition)
gives $d_2^2=0$ in Case~(ii)
(cf.\ \S\ref{sec:selection-principle}).

\smallskip
\emph{Step (e): Conclusion.}
By the Borcherds identity (axiom~(ii) of $\cA$), the cyclic
sum~\eqref{eq:case-ii-cyclic-sum} vanishes for every triple
$\{i,j,\ell\}$ and every choice of sections and forms.
Therefore $d_2^2 = 0$ on all Case~(ii) contributions.

\emph{Case (iii): Same pair} ($\{i,j\} = \{k,\ell\}$). Since $\text{Res}_{D_{ij}}$ extracts a simple pole along $D_{ij}$, applying it once produces a section regular along $D_{ij}$, and a second application yields zero: $\text{Res}_{D_{ij}}^2 = 0$.

\emph{Mixed terms.} The anticommutator $\{d_1, d_2\} = 0$
follows because the chiral product~$\mu$ is a morphism
of complexes: as a map of $\cD_X$-modules,
$\mu \colon j_* j^*(\cA \boxtimes \cA) \to \Delta_!(\cA)$
satisfies
\[
d_\cA \circ \mu = \mu \circ (d_\cA \boxtimes \id
  + \id \boxtimes d_\cA),
\]
the Leibniz rule (this is an axiom of a \emph{differential
graded} chiral algebra: the chiral product intertwines the
internal differential).  Since $d_{\mathrm{residue}}$ is
built from~$\mu$ via $\Res_{D_{ij}}$, the commutativity
$d_{\mathrm{internal}} \circ \Res_{D_{ij}}
= \Res_{D_{ij}} \circ d_{\mathrm{internal}}$ follows:
$\Res_{D_{ij}}$ is a $\cD_X$-module operation, and
$d_\cA$ is $\cD_X$-linear.

For $\{d_1, d_3\} = 0$: the operators $d_1$ and $d_3$ act on the algebra and form tensor factors respectively. The Koszul sign accompanying $d_3$ includes a factor $(-1)^{\sum_i |\phi_i|}$ from passing the de Rham differential past the algebra elements. After $d_1$ increases one algebra degree by $1$, the sign acquires an extra factor of $(-1)$. Thus $d_3 \circ d_1 = -d_1 \circ d_3$, and the anticommutator vanishes.

For $\{d_2, d_3\} = 0$: this follows from the residue exact sequence for logarithmic forms.  On a normal crossing divisor $D = \bigcup D_{ij} \subset \overline{C}_{n+1}(X)$, the residue map fits into the exact sequence $0 \to \Omega^k \to \Omega^k(\log D) \xrightarrow{\text{Res}} \bigoplus_{D_{ij}} \Omega^{k-1}_{D_{ij}}(\log D') \to 0$, and the de Rham differential is compatible with the residue map: $\text{Res}_{D_{ij}} \circ d_{\text{dR}} = d_{\text{dR}}|_{D_{ij}} \circ \text{Res}_{D_{ij}}$.  Since $d_2$ is a signed sum of residues and $d_3 = d_{\text{dR}}$, they anticommute (with signs from Convention~\ref{conv:orientations-enhanced}).
\end{proof}

\begin{remark}[Sign-level verification]\label{rem:sign-bridge}
For a complete sign-by-sign verification of $d^2 = 0$ at low degrees
(including the explicit computation for degree-3 elements $[a|b|c]$ in a
graded associative algebra), see Verification~\ref{ver:d2-degree3} and
Proposition~\ref{prop:master-sign} in Appendix~\ref{app:signs}.
\end{remark}

\begin{remark}[Synthesis]\label{rem:d-squared-synthesis}\label{rem:geometric-miracle}
The three mechanisms entering the proof of $d^2 = 0$,
the Borcherds identity (algebra), Stokes' theorem (topology), and
residue calculus (analysis), all arise from the boundary
stratification of $\overline{C}_n(X)$.  For the Heisenberg algebra,
this reduced to the Arnold relation
(\S\ref{sec:frame-bar-deg2}); in general, the factorization structure
on $\operatorname{Ran}(X)$ forces the compatibility
(Beilinson--Drinfeld~\cite{BD04};
see \S\ref{sec:selection-principle} for the selection principle).
\end{remark}

\begin{proposition}[Pole decomposition of the bar differential; \ClaimStatusProvedHere]\label{prop:pole-decomposition}
\index{bar differential!pole decomposition}
\index{bar differential!bracket component}
\index{bar differential!curvature component}
The residue differential $d_{\mathrm{res}}$ decomposes according to OPE pole order:
\begin{equation}\label{eq:pole-decomposition}
d_{\mathrm{res}} = d_{\mathrm{bracket}} + d_{\mathrm{curvature}}
\end{equation}
where $d_{\mathrm{bracket}}$ extracts residues from simple poles (Lie bracket terms $a_{(0)}b$) and $d_{\mathrm{curvature}}$ extracts residues from double poles (metric/level terms $\kappa(a,b)|0\rangle$).

This decomposition has the following properties:
\begin{enumerate}
\item $d_{\mathrm{bracket}}^2 \neq 0$ in general: the obstruction is the Borcherds associator, which involves iterated residues mixing both pole orders.
\item $d_{\mathrm{curvature}}^2 = 0$: double-pole residues produce scalars (vacuum vectors), and a second residue applied to a scalar vanishes.
\item $d_{\mathrm{res}}^2 = d_{\mathrm{bracket}}^2 + \{d_{\mathrm{bracket}}, d_{\mathrm{curvature}}\} + d_{\mathrm{curvature}}^2 = 0$, so the cross-term $\{d_{\mathrm{bracket}}, d_{\mathrm{curvature}}\}$ exactly compensates the failure of $d_{\mathrm{bracket}}^2 = 0$.
\end{enumerate}

In particular, the Lie-bracket Jacobi identity (which would give $d_{\mathrm{bracket}}^2 = 0$ for a Lie algebra) is \emph{insufficient} for nilpotency of the chiral bar differential.  The full Borcherds identity (associativity of the chiral product $\mu$, involving all pole orders simultaneously) is required.
\end{proposition}

\begin{proof}
For a chiral algebra $\cA$ with OPE $a(z)b(w) \sim \sum_{n \geq 0} a_{(n)}b \cdot (z-w)^{-n-1}$, the residue differential at the divisor $D_{ij}$ extracts:
\[
\mathrm{Res}_{D_{ij}}[\mu(\phi_i, \phi_j) \otimes \omega]
  = \mathrm{Res}_{\epsilon=0}\Bigl[\sum_{n \geq 0}
    \frac{(\phi_i)_{(n)}\phi_j}{\epsilon^{n+1}} \otimes \omega\Bigr]
\]
where $\epsilon = z_i - z_j$ is the local coordinate normal to $D_{ij}$.

The simple-pole contribution ($n = 0$) gives:
\[
d_{\mathrm{bracket}}(\cdots) = \sum_{i < j} (-1)^{\sigma_{ij}}
  \mathrm{Res}_{\epsilon=0}\Bigl[\frac{(\phi_i)_{(0)}\phi_j}{\epsilon}
    \otimes \omega\Bigr],
\]
which extracts the Lie bracket $[\phi_i, \phi_j] = (\phi_i)_{(0)}\phi_j$ via the simple-pole residue of $\omega$.

The double-pole contribution ($n = 1$) gives:
\[
d_{\mathrm{curvature}}(\cdots) = \sum_{i < j} (-1)^{\sigma_{ij}}
  \mathrm{Res}_{\epsilon=0}\Bigl[\frac{(\phi_i)_{(1)}\phi_j}{\epsilon^2}
    \otimes \omega\Bigr],
\]
which extracts the invariant bilinear form $(\phi_i)_{(1)}\phi_j = \kappa(\phi_i, \phi_j)|0\rangle$.  For Kac--Moody algebras, this is the level: $(J^a)_{(1)}J^b = k\,\delta^{ab}|0\rangle$.

\emph{Property~(2).}  Since $d_{\mathrm{curvature}}$ replaces a pair $(\phi_i, \phi_j)$ by a scalar multiple of the vacuum $|0\rangle$, the output of $d_{\mathrm{curvature}}$ at position $i$ is proportional to $|0\rangle$.  A subsequent application of $d_{\mathrm{curvature}}$ (or $d_{\mathrm{bracket}}$) involving this vacuum position produces $|0\rangle_{(n)}\phi_k = 0$ for $n \geq 0$, hence $d_{\mathrm{curvature}}^2 = 0$.

\emph{Property~(1).}  In the double sum $d_{\mathrm{bracket}}^2$, the one-overlap terms (Case~(ii) of Theorem~\ref{thm:bar-nilpotency-complete}) produce iterated residues $\mathrm{Res}_{D_{j\ell}}\mathrm{Res}_{D_{ij}}[(\phi_i)_{(0)}(\phi_j)_{(0)}\phi_\ell \otimes \omega]$.  The Borcherds identity for the chiral product asserts:
\begin{equation}\label{eq:borcherds-pole-mix}
\sum_{\text{cyclic}} \mathrm{Res}_{D_{j\ell}} \circ \mathrm{Res}_{D_{ij}}
  \bigl[\mu(\mu(\phi_i, \phi_j), \phi_\ell) \otimes \omega\bigr] = 0.
\end{equation}
Decomposing $\mu$ by pole order, the bracket--bracket contributions $(\phi_i)_{(0)}((\phi_j)_{(0)}\phi_\ell)$ give the Jacobi identity, but there are additional bracket--curvature cross-terms $(\phi_i)_{(0)}((\phi_j)_{(1)}\phi_\ell \cdot |0\rangle)$ and curvature--bracket terms that arise from the Taylor expansion of the OPE near the triple collision locus $D_{ij\ell}$.  The Jacobi identity cancels only the pure bracket terms; the cross-terms remain, giving $d_{\mathrm{bracket}}^2 \neq 0$.

\emph{Property~(3).}  The full Borcherds identity~\eqref{eq:borcherds-pole-mix} cancels \emph{all} iterated residue terms simultaneously, regardless of pole decomposition.  Since $d_{\mathrm{res}} = d_{\mathrm{bracket}} + d_{\mathrm{curvature}}$, the identity $d_{\mathrm{res}}^2 = 0$ (Theorem~\ref{thm:bar-nilpotency-complete}) together with $d_{\mathrm{curvature}}^2 = 0$ gives $d_{\mathrm{bracket}}^2 = -\{d_{\mathrm{bracket}}, d_{\mathrm{curvature}}\}$.
\end{proof}

\begin{remark}[Bicomplex obstruction]\label{rem:bicomplex-obstruction}
\index{bar complex!bicomplex structure}
Proposition~\ref{prop:pole-decomposition} shows that the pair $(d_{\mathrm{bracket}}, d_{\mathrm{curvature}})$ does \emph{not} form a bicomplex (which would require $d_{\mathrm{bracket}}^2 = d_{\mathrm{curvature}}^2 = \{d_{\mathrm{bracket}}, d_{\mathrm{curvature}}\} = 0$).  Instead, $d_{\mathrm{bracket}}^2 = -\{d_{\mathrm{bracket}}, d_{\mathrm{curvature}}\} \neq 0$: the curvature (level/central charge) is the \emph{obstruction} to the Lie-bracket differential being nilpotent.

For \emph{free fields} (Heisenberg, free fermion), the OPE has only a double pole ($a_{(0)}b = 0$), so $d_{\mathrm{bracket}} = 0$ and $d_{\mathrm{res}} = d_{\mathrm{curvature}}$, which squares to zero automatically.  This explains the simpler algebraic structure of free-field bar complexes (Corollary~\ref{cor:subexp-free-field}).

For Kac--Moody algebras, the failure of $d_{\mathrm{bracket}}^2 = 0$ is controlled by the level-$k$ double-pole OPE coefficient $k \cdot (\,,\,)$, which gives rise to the curved $A_\infty$ curvature element $m_0 \propto (k+h^\vee)\kappa/(2h^\vee)$ (Chapter~\ref{chap:deformation-theory}).
\end{remark}

\begin{corollary}[Bar complex is functorial; \ClaimStatusProvedHere]\label{cor:bar-functorial}
The bar construction $\bar{B}^{\bullet}(-)$ is a functor from chiral algebras to differential graded vector spaces:
\[\bar{B}^{\bullet}: \mathsf{ChiralAlg}(\Sigma_g) \to \mathsf{dgVect}\]

Moreover:
\begin{enumerate}
\item A morphism $f: \mathcal{A} \to \mathcal{A}'$ of chiral algebras induces a chain map $\bar{B}^{\bullet}(f): \bar{B}^{\bullet}(\mathcal{A}) \to \bar{B}^{\bullet}(\mathcal{A}')$
\item The bar construction preserves quasi-isomorphisms: a quasi-isomorphism $f$ induces a quasi-isomorphism $\bar{B}(f)$ by the filtration spectral sequence argument of Theorem~\ref{thm:bar-nilpotency-complete}
\item Composition is preserved: $\bar{B}^{\bullet}(g \circ f) = \bar{B}^{\bullet}(g) \circ \bar{B}^{\bullet}(f)$
\end{enumerate}
\end{corollary}

\begin{proof}
Since $d^2 = 0$, the bar complex $(\bar{B}^{\bullet}(\mathcal{A}), d)$ is a genuine chain complex.

For a morphism $f: \mathcal{A} \to \mathcal{A}'$, define:
\[\bar{B}^n(f)(\phi_0 \otimes \cdots \otimes \phi_n \otimes \omega) = f(\phi_0) \otimes \cdots \otimes f(\phi_n) \otimes \omega\]

This commutes with the differential:
\[d \circ \bar{B}^n(f) = \bar{B}^n(f) \circ d\]

because $f$ is a morphism of chiral algebras (preserves the chiral product $\mu$).

The remaining properties (functoriality in morphisms, compatibility with composition) follow from the universal property of the cofree coalgebra \cite[Section~1.2]{LV12}.
\end{proof}

\subsection{Stokes' theorem on configuration spaces}

\begin{theorem}[Stokes' theorem on configuration spaces; \ClaimStatusProvedHere]\label{thm:stokes-config}
For the Fulton--MacPherson compactification $\overline{C}_{n+1}(\Sigma_g)$ with boundary divisor $D = \bigcup_{i<j} D_{ij}$:

For any $\omega \in \Omega^k(\overline{C}_{n+1}(\Sigma_g))$ (a smooth $k$-form):
\[\int_{\overline{C}_{n+1}(\Sigma_g)} d_{\text{dR}}(\omega) = \sum_{i<j} \epsilon_{ij} \int_{D_{ij}} \omega|_{D_{ij}}\]
where $\epsilon_{ij} = \pm 1$ is the orientation sign.

For logarithmic forms $\omega \in \Omega^k(\log D)$:
\[\int_{\overline{C}_{n+1}} d_{\text{dR}}(\omega) = \sum_{i<j} \epsilon_{ij} \int_{D_{ij}} \text{Res}_{D_{ij}}(\omega)\]
\end{theorem}

\begin{proof}
The configuration space $\overline{C}_{n+1}(\Sigma_g)$ is a \emph{manifold with corners}. The boundary consists of multiple smooth divisors $D_{ij}$ meeting transversely along higher codimension strata.

Stokes' theorem for manifolds with corners (Theorem of Melrose, Mazzeo, et al.) states:
\[\int_M d\omega = \sum_{\text{faces } F} \epsilon_F \int_F \omega|_F\]
where faces are the codimension-1 boundary components.

\emph{Step 1: Identify faces}

The faces of $\overline{C}_{n+1}(\Sigma_g)$ are precisely the divisors $D_{ij}$ for $i < j$.

Codimension: Each $D_{ij}$ has codimension 1 in $\overline{C}_{n+1}$:
\[\dim_{\mathbb{C}} D_{ij} = \dim_{\mathbb{C}} \overline{C}_{n+1} - 1 = (n+1) - 1 = n\]

\emph{Step 2: Orientation of faces}

Each face $D_{ij}$ inherits an orientation from the \emph{outward normal} convention (Convention \ref{conv:orientations-enhanced}):
\[\text{or}(D_{ij}) = d\epsilon_{ij} \wedge \text{or}_{\text{tangent}}\]
where $\epsilon_{ij} = |z_i - z_j|$ increases towards the interior.

The sign $\epsilon_{ij}$ in Stokes' theorem is:
\[\epsilon_{ij} = +1 \quad \text{if } \text{or}(D_{ij}) = \text{outward normal orientation}\]
\[\epsilon_{ij} = -1 \quad \text{if opposite}\]

With our conventions: $\epsilon_{ij} = +1$ for all $i < j$.

\emph{Step 3: Corners}

The divisors $D_{ij}$ and $D_{k\ell}$ (for distinct pairs) intersect along codimension-2 strata:
\[D_{ij} \cap D_{k\ell} = D_{ijk\ell}\]

At these corners, we must verify that contributions from different faces cancel appropriately.

Consider the corner $D_{ijk} = D_{ij} \cap D_{jk}$ (where three points collide). Approaching from different faces:

From $D_{ij}$:
\[\text{contribution} = \int_{D_{ijk}} \omega|_{D_{ij}}|_{D_{ijk}} \cdot \epsilon_{jk|D_{ij}}\]

From $D_{jk}$:
\[\text{contribution} = \int_{D_{ijk}} \omega|_{D_{jk}}|_{D_{ijk}} \cdot \epsilon_{ij|D_{jk}}\]

By Lemma~\ref{lem:orientation} (orientation consistency), these have opposite signs:
\[\epsilon_{jk|D_{ij}} = -\epsilon_{ij|D_{jk}}\]

So the corner contributions cancel.

\emph{Step 4: Apply Stokes' theorem}

With corners handled correctly:
\[\int_{\overline{C}_{n+1}} d_{\text{dR}}(\omega) = \sum_{i<j} \int_{D_{ij}} \omega|_{D_{ij}}\]

For logarithmic forms, $\omega|_{D_{ij}}$ is not well-defined (it has a pole), but $\text{Res}_{D_{ij}}(\omega)$ is:
\[\int_{\overline{C}_{n+1}} d_{\text{dR}}(\omega) = \sum_{i<j} \int_{D_{ij}} \text{Res}_{D_{ij}}(\omega)\]
\end{proof}

\begin{example}[Stokes for three points]\label{ex:stokes-three-points}
Consider $\overline{C}_3(\mathbb{C})$ (three points on the complex plane, compactified).

\emph{Boundary.} $D = D_{12} \cup D_{23} \cup D_{13}$ (three divisors)

\emph{2-form.} $\omega = \eta_{12} \wedge \eta_{23}$ (logarithmic 2-form)

\emph{Differential.} 
\begin{align*}
d_{\text{dR}}(\eta_{12} \wedge \eta_{23}) &= d(\eta_{12}) \wedge \eta_{23} - \eta_{12} \wedge d(\eta_{23}) \\
&= 0
\end{align*}
(since $d(\eta_{ij}) = 0$ for logarithmic 1-forms)

\emph{Stokes.}
\[\int_{\overline{C}_3} d_{\text{dR}}(\omega) = 0 = \int_{D_{12}} \text{Res}_{D_{12}}(\omega) + \int_{D_{23}} \text{Res}_{D_{23}}(\omega) + \int_{D_{13}} \text{Res}_{D_{13}}(\omega)\]

\emph{Residues.}
- $\text{Res}_{D_{12}}(\eta_{12} \wedge \eta_{23}) = \eta_{23}|_{D_{12}}$
- $\text{Res}_{D_{23}}(\eta_{12} \wedge \eta_{23}) = -\eta_{12}|_{D_{23}}$ (sign from wedge order)
- $\text{Res}_{D_{13}}(\eta_{12} \wedge \eta_{23}) = 0$ (no pole along $D_{13}$)

Therefore
\[0 = \int_{D_{12}} \eta_{23} - \int_{D_{23}} \eta_{12} + 0\]

This is the \emph{Arnold relation}:
\[\eta_{12} \wedge \eta_{23} \text{ integrates to zero around boundaries}\]
\end{example}

\begin{corollary}[Residues anticommute at corners; \ClaimStatusProvedHere]\label{cor:residues-anticommute}
For transverse divisors $D_{ij}$ and $D_{k\ell}$ meeting at a codimension-2 stratum:
\[\text{Res}_{D_{ij}} \text{Res}_{D_{k\ell}} + \text{Res}_{D_{k\ell}} \text{Res}_{D_{ij}} = 0\]
(up to sign)
\end{corollary}

\begin{proof}
Since $D_{ij}$ and $D_{k\ell}$ meet transversally at the codimension-2 stratum $D_{ij} \cap D_{k\ell}$, we may choose local coordinates $(u,v, \ldots)$ near the intersection with $D_{ij} = \{u = 0\}$ and $D_{k\ell} = \{v = 0\}$.  For a logarithmic form $\omega$ with at most simple poles along both divisors, the iterated residue $\mathrm{Res}_{v=0}\,\mathrm{Res}_{u=0}\,\omega$ extracts the coefficient of $d\log u \wedge d\log v$, while $\mathrm{Res}_{u=0}\,\mathrm{Res}_{v=0}\,\omega$ extracts the coefficient of $d\log v \wedge d\log u = -d\log u \wedge d\log v$.  Hence $\mathrm{Res}_{D_{ij}} \circ \mathrm{Res}_{D_{k\ell}} = -\mathrm{Res}_{D_{k\ell}} \circ \mathrm{Res}_{D_{ij}}$.
\end{proof}

\subsection{Arnold relations: proofs from three perspectives}

\begin{convention}[Set ordering and position notation]\label{conv:set-ordering-arnold}
Throughout this manuscript, we adopt the following conventions for ordered sets:

\begin{enumerate}
\item \emph{Natural Ordering:} For any finite subset $S \subseteq \mathbb{N}$, 
we always use the ordering inherited from $\mathbb{N}$:
\[S = \{k_1, k_2, \ldots, k_m\} \quad \text{where} \quad k_1 < k_2 < \cdots < k_m\]

\item \emph{Position Function:} For $k \in S$, we denote by $|k|_S$ (or simply $|k|$ 
when $S$ is clear from context) the \emph{position} of $k$ in this ordering:
\[k = k_{|k|} \quad \iff \quad |k| = i \text{ where } k \text{ is the } i\text{-th smallest element of } S\]

\item \emph{Sign Convention:} Signs arising from reordering are computed via the 
Koszul rule. Moving an element $k$ past position $|k|$ introduces sign $(-1)^{|k|-1}$.

\item \emph{Multi-indices:} For multi-index sets (e.g., in partitions), we use 
lexicographic ordering.
\end{enumerate}

\emph{Example.} For $S = \{2, 5, 7\}$:
\begin{itemize}
\item $|2|_S = 1$ (first position)
\item $|5|_S = 2$ (second position)  
\item $|7|_S = 3$ (third position)
\end{itemize}

In Arnold relations, the notation $(-1)^{|k|}$ means $(-1)^{|k|_S}$ where $S$ is the 
index set of the collision divisor under consideration.
\end{convention}

\begin{theorem}[Arnold relations; \ClaimStatusProvedHere]\label{thm:arnold-three}
\index{Arnold relations|textbf}
We encountered these relations concretely in the Heisenberg bar complex (\S\ref{sec:frame-bar-deg2}), where they appeared as the identity forcing $d^2 = 0$ at degree~$2$.  In full generality:

For distinct indices $i, j, k \in \{1, \ldots, n\}$, the logarithmic 1-forms $\eta_{ij} = d\log(z_i - z_j)$ satisfy:

\emph{Formulation 1 (basic).}
\[\eta_{ij} \wedge \eta_{jk} + \eta_{jk} \wedge \eta_{ki} + \eta_{ki} \wedge \eta_{ij} = 0\]

\emph{Formulation 2 (Orlik--Solomon).}
The algebra $H^*(C_n(\mathbb{C}); \mathbb{Q})$ is the quotient of the exterior algebra $\bigwedge\langle \eta_{ij} \mid 1 \le i < j \le n \rangle$ by the ideal generated by the three-term Arnold relations of Formulation~1.  All higher-degree relations in the Orlik--Solomon algebra follow from these by repeated application; there is no independent ``general Arnold relation'' beyond the three-term version.

\emph{Formulation 3 (cohomological).}
The cohomology ring $H^*(\overline{C}_n(X); \mathbb{Q})$ is generated by classes $[\eta_{ij}]$ subject to the Arnold relations.
\end{theorem}

\begin{proof}
See Theorem~\ref{thm:arnold-relations} for the partial-fractions proof.
The topological, combinatorial, and operadic perspectives are developed in \S\ref{sec:arnold-three-proofs-comprehensive}.
\end{proof}

\begin{remark}[Arnold relations = Jacobi identity]\label{rem:arnold-jacobi-geometric}
The geometric content of $\dzero^2 = 0$ at degree~$3$ is precisely the Jacobi identity: the three boundary strata of $\overline{C}_4(\mathbb{P}^1)$ that contribute to $\dzero^2$ correspond to the three terms of the Jacobi identity for the chiral bracket.  Concretely, the Arnold relation $\eta_{12} \wedge \eta_{23} + \eta_{23} \wedge \eta_{31} + \eta_{31} \wedge \eta_{12} = 0$ forces
\[
{f^{ab}}_d\,{f^{dc}}_e + {f^{bc}}_d\,{f^{da}}_e + {f^{ca}}_d\,{f^{db}}_e = 0,
\]
which is the Jacobi identity for the structure constants extracted by residues.  The implication is bidirectional: the Arnold relations \emph{are} the Jacobi identity via the residue dictionary.  See Computation~\ref{comp:geom-alg-comparison-deg3} for the complete term-by-term verification in $\widehat{\mathfrak{sl}}_{2,k}$ and Theorem~\ref{thm:arnold-jacobi} for the general CFT formulation.
\end{remark}

\begin{corollary}[Cohomology of configuration spaces; \ClaimStatusProvedElsewhere]\label{cor:cohomology-config}
The cohomology ring $H^*(C_n(\mathbb{C}); \mathbb{Q})$ of the open configuration space is:
\[H^*(C_n(\mathbb{C})) \cong \mathbb{Q}[\eta_{ij} : 1 \leq i < j \leq n] / \mathcal{I}_{\text{Arnold}}\]
where $\mathcal{I}_{\text{Arnold}}$ is the ideal generated by Arnold relations.
\end{corollary}

\begin{proof}
By Arnol'd~\cite{Arnold69}, the 1-forms $\eta_{ij} = d\log(z_i - z_j)$ generate $H^*(C_n(\mathbb{C}); \mathbb{Q})$ and satisfy the Arnold relations $\eta_{ij} \wedge \eta_{jk} + \eta_{jk} \wedge \eta_{ki} + \eta_{ki} \wedge \eta_{ij} = 0$.  That these generate \emph{all} relations follows from Cohen's computation of $H^*(C_n(\mathbb{C}))$ as the cohomology of the Arnol'd--Brieskorn braid arrangement complement~\cite{Coh76}.  See also Appendix~\ref{app:arnold-relations} for the three proofs of the Arnold relations used in this monograph.
\end{proof}

\subsection{Low-degree explicit computations}

\subsubsection{Degree 0: the vacuum}

\begin{computation}[Degree 0; \ClaimStatusProvedHere]\label{comp:deg0}
In degree 0:
\[\bar{B}^0(\mathcal{A}) = \Gamma\left(\overline{C}_1(\Sigma_g), \mathcal{A} \otimes \Omega^0(\log D)\right)\]

But $\overline{C}_1(\Sigma_g) = \Sigma_g$ (single point, no collisions), and $\Omega^0(\log D) = \mathcal{O}_{\Sigma_g}$ (functions).

Therefore
\[\bar{B}^0(\mathcal{A}) = \Gamma(\Sigma_g, \mathcal{A}) = H^0(\Sigma_g, \mathcal{A})\]

This is the space of global sections of the chiral algebra.

\emph{Physical interpretation.} This is the vacuum sector: states with no operator insertions.

\emph{Differential.} $d: \bar{B}^0 \to \bar{B}^{-1}$. But there is no $\bar{B}^{-1}$ (negative degree), so $d|_{\bar{B}^0} = 0$.
\end{computation}

\subsubsection{Degree 1: two-point functions}

\begin{computation}[Degree 1; \ClaimStatusProvedHere]\label{comp:deg1-general}
In degree 1:
\[\bar{B}^1(\mathcal{A}) = \Gamma\left(\overline{C}_2(\Sigma_g), j_*j^*(\mathcal{A} \boxtimes \mathcal{A}) \otimes \Omega^1(\log D_{12})\right)\]

\emph{Configuration space.} $\overline{C}_2(\Sigma_g)$ parametrizes two points on $\Sigma_g$.
- At genus 0: After modding out $\text{PSL}_2$, $\overline{C}_2(\mathbb{P}^1) \cong \mathbb{P}^1$
- At genus $g \geq 1$: $\overline{C}_2(\Sigma_g)$ is more complex (includes period matrix data)

\emph{Logarithmic 1-forms.} $\Omega^1(\log D_{12})$ is 1-dimensional, spanned by:
\[\eta_{12} = \frac{dz_1 - dz_2}{z_1 - z_2} = d\log(z_1 - z_2)\]

\emph{Basis.} A basis for $\bar{B}^1(\mathcal{A})$ is:
\[\{\phi_i(z_1) \otimes \phi_j(z_2) \otimes \eta_{12} : \phi_i, \phi_j \in \mathcal{A}\}\]

If $\mathcal{A}$ has $N$ generators, then:
\[\dim \bar{B}^1(\mathcal{A}) = N^2\]

\emph{Differential.} $d: \bar{B}^1 \to \bar{B}^0$
\[d(\phi_i \otimes \phi_j \otimes \eta_{12}) = \text{Res}_{D_{12}}[\mu(\phi_i, \phi_j) \otimes \eta_{12}]\]

where $\mu$ is the chiral product (OPE).

If the OPE is:
\[\phi_i(z)\phi_j(w) = \sum_k \frac{C_{ij}^k}{(z-w)^{\Delta_k}} \phi_k(w) + \text{regular}\]

then the bar differential acts by extracting the chiral product $\mu$:
\[d_{\mathrm{res}}(\phi_i \otimes \phi_j \otimes \eta_{12}) = \mu(\phi_i, \phi_j) = \operatorname{Res}_{z=w}\left[\phi_i(z)\phi_j(w)\,dz\right]\]
The Cauchy residue picks out the coefficient of the simple pole $(z-w)^{-1}$ in the OPE.  For a term $C_{ij}^k \phi_k(w)/(z-w)^{\Delta_k}$:
\begin{itemize}
\item $\Delta_k = 1$ (simple pole): $\operatorname{Res}_{z=w}[C_{ij}^k \phi_k/(z{-}w) \cdot dz] = C_{ij}^k \phi_k$
\item $\Delta_k \geq 2$ (higher pole): $\operatorname{Res}$ gives derivatives of $\phi_k$, contributing to secondary operations
\item $\Delta_k = 0$ (regular): no pole, zero contribution
\end{itemize}
\emph{Warning.} One must \emph{not} multiply the OPE pole by the propagator $\eta_{12} = d\epsilon/\epsilon$ and take the combined residue; the logarithmic form $\eta_{12}$ accounts for the \emph{degree} in the bar complex, not an additional pole (see Part~II for the careful calculation).
\end{computation}

\begin{example}[Heisenberg at degree 1]\label{ex:heisenberg-deg1-complete}
The Heisenberg bar differential vanishes at degree~$1$
(Example~\ref{ex:heisenberg-d-deg1}):
$d_{\mathrm{res}}(J \otimes J \otimes \eta_{12}) = 0$
because the double pole produces a triple-pole residue.
The class
$[J \otimes J \otimes \eta_{12}]
\in H^1(\bar{B}^{\bullet}(\mathcal{H}))$
is non-trivial; the central charge~$k$ appears only at
genus~$1$.
\end{example}

\begin{example}[\texorpdfstring{$\beta\gamma$}{beta-gamma} system at degree 1]\label{ex:betagamma-deg1}
For the $\beta\gamma$ system with generators $\beta(z), \gamma(z)$ and OPE:
\[\beta(z)\gamma(w) = \frac{1}{z-w} + \text{regular}, \quad \beta(z)\beta(w) = 0, \quad \gamma(z)\gamma(w) = 0\]

\emph{Bar degree 1.}
\[\bar{B}^1(\mathcal{FG}) = \text{span}\{\beta \otimes \beta \otimes \eta, \beta \otimes \gamma \otimes \eta, \gamma \otimes \beta \otimes \eta, \gamma \otimes \gamma \otimes \eta\}\]

\emph{Differential.} Only the $\beta \otimes \gamma$ term contributes:
\begin{align*}
d(\beta \otimes \gamma \otimes \eta_{12}) &= \text{Res}_{D_{12}}\bigl[\mu(\beta, \gamma) \otimes \eta_{12}\bigr] \\
&= \bigl[\text{Res}_{\epsilon=0}\,\eta_{12}\bigr] \cdot \mu(\beta, \gamma)\big|_{z_1=z_2}
\end{align*}
Setting $\epsilon = z_1 - z_2$, the propagator is $\eta_{12} = d\epsilon/\epsilon$, which has $\text{Res}_{\epsilon=0}[d\epsilon/\epsilon] = 1$. The chiral product $\mu(\beta, \gamma)$ extracts the simple-pole OPE coefficient $\beta(z)\gamma(w) \sim 1/(z-w)$, giving $\mathbb{1}$ (the unit element). Hence $d(\beta \otimes \gamma \otimes \eta_{12}) = \mathbb{1}$.

(Note: the residue is of the \emph{logarithmic} 1-form $d\epsilon/\epsilon$, not of $d\epsilon/\epsilon^2$; one must not multiply the OPE pole by the propagator pole.)

Similarly: $d(\gamma \otimes \beta \otimes \eta_{12}) = -\mathbb{1}$ (the sign arises from the OPE $\gamma(z)\beta(w) \sim -1/(z-w)$, which carries a sign relative to $\beta(z)\gamma(w) \sim +1/(z-w)$ from the ordering convention for the chiral product, not from any fermionic anticommutativity; the $\beta\gamma$ system is bosonic).

\emph{Cohomology.} $H^1(\bar{B}^{\bullet}(\mathcal{FG})) = \text{span}\{\beta \otimes \beta, \gamma \otimes \gamma\}$ (2-dimensional).
\end{example}

\begin{remark}[Intuition \`{a} la Witten across genera]
In 2d CFT, correlation functions of chiral operators $\phi_1(z_1), \ldots, \phi_n(z_n)$ are computed by the genus expansion:
\[
\langle \phi_1(z_1) \cdots \phi_n(z_n) \rangle = \sum_{g=0}^{\infty} \lambda^{2g-2} \int_{\text{field space}} \mathcal{D}\phi \, e^{-S[\phi]} \phi_1(z_1) \cdots \phi_n(z_n)
\]
The singularities as $z_i \to z_j$ encode the operator algebra structure at each genus. Mathematically, the configuration space $C_n(\Sigma_g) = \Sigma_g^n \setminus \{\text{diagonals}\}$ parametrizes non-colliding insertion points; its FM compactification $\overline{C}_n(\Sigma_g)$ adds collision strata and degenerating cycles; logarithmic forms $d\log(z_i - z_j)$ carry OPE singularities with genus corrections; and the bar differential computes quantum corrections via residues and period integrals, each genus contributing specific modular forms.
\end{remark}

\begin{definition}[Orientation line bundle]\label{def:orientation}
The \emph{orientation line bundle} $\text{or}_{p+1}^{(g)}$ on $\overline{C}_{p+1}(\Sigma_g)$ is defined as:
\[
\text{or}_{p+1}^{(g)} = \det(T\overline{C}_{p+1}(\Sigma_g)) \otimes \text{sgn}_{p+1} \otimes \mathcal{L}_g
\]
where:
\begin{itemize}
\item $\det(T\overline{C}_{p+1}(\Sigma_g))$ is the top exterior power of the tangent bundle
\item $\text{sgn}_{p+1}$ is the sign representation of $\mathfrak{S}_{p+1}$
\item $\mathcal{L}_g$ is the genus-dependent orientation bundle from period matrix
\item The tensor product ensures that exchanging two points introduces a sign and modular covariance
\end{itemize}
This ensures $d^2 = 0$ with consistent signs across all face maps and genus levels.
\end{definition}

\subsection{Explicit low-degree terms}

\begin{example}[Bar complex in low degrees]
\begin{align}
\bar{B}^0(\mathcal{A}) &= \mathcal{A} \\
\bar{B}^1(\mathcal{A}) &= \Gamma(C_2(X), \mathcal{A} \boxtimes \mathcal{A} \otimes \eta_{12}) \\
\bar{B}^2(\mathcal{A}) &= \Gamma(\overline{C}_3(X), \mathcal{A}^{\boxtimes 3} \otimes \Omega^2_{\log})
\end{align}

The bar differential lowers bar degree.  Here bar degree~$n$ uses sections over $C_{n+1}(X)$; the display above shows the \emph{unreduced} complex with $\bar{B}^0 = \mathcal{A}$.  The \emph{reduced} bar complex, used from \S\ref{subsec:bar-functoriality} onward, replaces $\mathcal{A}$ by its augmentation ideal $\bar{\mathcal{A}} = \ker(\varepsilon \colon \mathcal{A} \to \omega_X)$ and starts at $\bar{B}^0 = \mathbb{C}$.  Augmentation separates generators from scalars: the map~$\varepsilon$ extracts the component of each operator proportional to the identity (the vacuum expectation value), and the reduced complex $T^c(s^{-1}\bar{\mathcal{A}})$ tensors together only the non-scalar modes.  Without this splitting, the reduced coproduct on the bar coalgebra would not be conilpotent, and the cofree coalgebra structure that drives the bar-cobar adjunction (Theorem~\ref{thm:bar-cobar-adjunction}) would be unavailable.
\begin{align}
d: \bar{B}^1 &\to \bar{B}^0 \\
a_1 \otimes a_2 \otimes \eta_{12} &\mapsto \text{Res}_{z_1=z_2}[a_1(z_1) \cdot a_2(z_2) \cdot \eta_{12}]
\end{align}
This residue extraction computes the OPE product, contracting two operator insertions via the singular part of their operator product.
\end{example}

\subsection{Functoriality of the bar construction}
\label{subsec:bar-functoriality}
\index{bar-cobar!functoriality}

\begin{theorem}[Bar construction is functorial; \ClaimStatusProvedHere]\label{thm:bar-functorial-complete}
\label{thm:bar-functorial}
The geometric bar construction defines a functor:
\[\bar{B}^{\text{geom}}: \mathsf{ChirAlg}_X^{\mathrm{aug}} \to \mathsf{dgCoalg}_X\]
from augmented chiral algebras to dg coalgebras, that is:
\begin{enumerate}
\item \emph{Well-defined on objects:} For each augmented chiral algebra $\mathcal{A}$, $\bar{B}^{\text{geom}}(\mathcal{A})$ is a differential graded coalgebra
\item \emph{Well-defined on morphisms:} For each morphism $f: \mathcal{A} \to \mathcal{B}$ of augmented chiral algebras, there is an induced coalgebra morphism $\bar{B}^{\text{geom}}(f): \bar{B}^{\text{geom}}(\mathcal{A}) \to \bar{B}^{\text{geom}}(\mathcal{B})$
\item \emph{Preserves identities:} $\bar{B}^{\text{geom}}(\text{id}_\mathcal{A}) = \text{id}_{\bar{B}^{\text{geom}}(\mathcal{A})}$
\item \emph{Preserves composition:} $\bar{B}^{\text{geom}}(g \circ f) = \bar{B}^{\text{geom}}(g) \circ \bar{B}^{\text{geom}}(f)$
\end{enumerate}
\end{theorem}

\begin{proof}
Well-definedness on objects is
Theorem~\ref{thm:bar-nilpotency-complete}.
For a morphism $f\colon \cA \to \cB$ of augmented chiral
algebras, define
$\bar{B}^{\mathrm{geom}}(f)(a_0 \otimes \cdots \otimes a_n
\otimes \omega) = f(a_0) \otimes \cdots \otimes f(a_n) \otimes
\omega$\label{def:bar-induced-map}
(apply $f$ to algebra factors, leave forms unchanged).

\emph{Chain map property.}\label{lem:bar-induced-chain-map}
Since $f$ commutes with the internal differential ($f$ is a
$\mathcal{D}$-module map), with the residue differential ($f$
preserves the chiral product), and does not affect the de~Rham
component, $\bar{B}^{\mathrm{geom}}(f)$ commutes with
$d = d_{\mathrm{int}} + d_{\mathrm{res}} + d_{\mathrm{dR}}$.

\emph{Coalgebra morphism.}\label{lem:bar-induced-coalgebra}
The coproduct $\Delta$ is defined by restricting to collision
divisors; since $f$ acts on algebra factors and $\Delta$ acts
on the indexing set,
$\Delta \circ \bar{B}(f) = (\bar{B}(f) \otimes \bar{B}(f))
\circ \Delta$.  The counit compatibility and preservation of
identities and composition are immediate from the definition.
\end{proof}

\begin{corollary}[Natural transformation property; \ClaimStatusProvedHere]\label{cor:bar-natural}
\label{cor:why-functoriality}
A commutative diagram of chiral algebras induces a commutative diagram of bar complexes: if $k \circ f = g \circ h$ in $\mathsf{ChirAlg}_X$, then $\bar{B}(k) \circ \bar{B}(f) = \bar{B}(g) \circ \bar{B}(h)$ in $\mathsf{dgCoalg}_X$.  This is immediate from functoriality.
\end{corollary}

\begin{proposition}[Model independence; \ClaimStatusProvedHere]
\label{prop:model-independence}
\index{model independence}
Let $\cA$ be a chiral algebra on~$X$.
Any two admissible\footnote{An admissible presentation is a
dg factorization coalgebra computing $\bar{B}_X(\cA)$ in the homotopy
category: it is built from sections of $\cA^{\boxtimes(n+1)}$ over
open substacks of $\operatorname{Ran}(X)$ and its differential restricts
to the collision-residue map on each boundary stratum.}
dg presentations of the bar object
$\mathcal{B}_X(\cA)$ are connected by a contractible space of
quasi-isomorphisms.  In particular, any two such models give
canonically isomorphic cohomology, spectral sequences, and generating
functions.
\end{proposition}

\begin{proof}
Both presentations are cofibrant-fibrant objects in the model structure
on conilpotent dg coalgebras over $\operatorname{Ran}(X)$
(Positselski~\cite{Positselski11}, Theorem~8.1).  Cofibrant-fibrant
replacements in this model structure are unique up to a contractible
space of weak equivalences: the mapping space
$\operatorname{Map}(B_1, B_2)$ between two such replacements is
contractible whenever both compute the same homotopy object.
The configuration-space model $\bar{B}_X(\cA)$ is cofibrant by
freeness of the coalgebra generators and fibrant by the Cousin
filtration (Theorem~\ref{thm:chevalley-cousin}).  Any other admissible
model shares these properties by the same arguments, whence the
mapping space between them is contractible.
\end{proof}

\subsection{Coalgebra structure}

\begin{theorem}[Bar coalgebra; \ClaimStatusProvedHere]\label{thm:bar-coalgebra}
The bar complex carries a natural coalgebra structure:
\[\Delta: \bar{B}^{\text{geom}}(\mathcal{A}) \to \bar{B}^{\text{geom}}(\mathcal{A}) \otimes \bar{B}^{\text{geom}}(\mathcal{A})\]
induced by the diagonal map $X \to X \times X$.
\end{theorem}

\begin{proof}
Define $\Delta$ on tensors by summing over ordered bipartitions of the input
index set and restricting the logarithmic form to the corresponding boundary
factorization stratum, as in the explicit formula used in
Theorem~\ref{thm:coassociativity-complete}. This defines a morphism
$\bar{B}^{\mathrm{geom}}(\mathcal{A})\to
\bar{B}^{\mathrm{geom}}(\mathcal{A})\otimes\bar{B}^{\mathrm{geom}}(\mathcal{A})$.

Coassociativity of this coproduct is proved in
Theorem~\ref{thm:coassociativity-complete}; counit compatibility is proved in
Theorem~\ref{thm:counit-axioms}. Hence the stated coproduct gives a coalgebra
structure on $\bar{B}^{\mathrm{geom}}(\mathcal{A})$.
\end{proof}

\subsection{Coalgebra axioms: verification}
\label{subsec:coalgebra-axioms-complete}

\begin{theorem}[Coassociativity; \ClaimStatusProvedHere]\label{thm:coassociativity-complete}
\index{coassociativity}
The coproduct $\Delta: \bar{B}_n(\mathcal{A}) \to \bigoplus_{p+q=n} \bar{B}_p(\mathcal{A}) \otimes \bar{B}_q(\mathcal{A})$ is coassociative:
\[(\Delta \otimes \text{id}) \circ \Delta = (\text{id} \otimes \Delta) \circ \Delta\]
\end{theorem}

\begin{proof}

\subsection*{Step 1: definition of coproduct}

Recall that the coproduct on $\bar{B}_n(\mathcal{A})$ is defined by: for $(a_0 \otimes \cdots \otimes a_n \otimes \omega) \in \bar{B}_n(\mathcal{A})$,
\[\Delta(a_0 \otimes \cdots \otimes a_n \otimes \omega) = \sum_{I \sqcup J = [0,n]} (a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J)\]
where:
\begin{itemize}
\item $I, J \subseteq [0,n]$ partition the index set
\item $a_I = a_{i_0} \otimes \cdots \otimes a_{i_p}$ for $I = \{i_0, \ldots, i_p\}$
\item $\omega_I$ is the restriction of $\omega$ to the configuration space $\overline{C}_{|I|}(X)$
\end{itemize}

\subsection*{Step 2: left side - $(\Delta \otimes \text{id}) \circ \Delta$}

Apply $\Delta$ first:
\[\Delta(a_0 \otimes \cdots \otimes a_n \otimes \omega) = \sum_{I \sqcup J = [0,n]} (a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J)\]

Now apply $\Delta \otimes \text{id}$ to each term:
\begin{align*}
&(\Delta \otimes \text{id})\left((a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J)\right) \\
&= \Delta(a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J) \\
&= \left(\sum_{I' \sqcup I'' = I} (a_{I'} \otimes \omega_{I'}) \otimes (a_{I''} \otimes \omega_{I''})\right) \otimes (a_J \otimes \omega_J) \\
&= \sum_{I' \sqcup I'' = I} (a_{I'} \otimes \omega_{I'}) \otimes (a_{I''} \otimes \omega_{I''}) \otimes (a_J \otimes \omega_J)
\end{align*}

Summing over all partitions $I \sqcup J = [0,n]$:
\[(\Delta \otimes \text{id}) \circ \Delta = \sum_{I' \sqcup I'' \sqcup J = [0,n]} (a_{I'} \otimes \omega_{I'}) \otimes (a_{I''} \otimes \omega_{I''}) \otimes (a_J \otimes \omega_J)\]

\subsection*{Step 3: right side - $(\text{id} \otimes \Delta) \circ \Delta$}

Apply $\Delta$ first (same as before):
\[\Delta(a_0 \otimes \cdots \otimes a_n \otimes \omega) = \sum_{I \sqcup J = [0,n]} (a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J)\]

Now apply $\text{id} \otimes \Delta$:
\begin{align*}
&(\text{id} \otimes \Delta)\left((a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J)\right) \\
&= (a_I \otimes \omega_I) \otimes \Delta(a_J \otimes \omega_J) \\
&= (a_I \otimes \omega_I) \otimes \left(\sum_{J' \sqcup J'' = J} (a_{J'} \otimes \omega_{J'}) \otimes (a_{J''} \otimes \omega_{J''})\right) \\
&= \sum_{J' \sqcup J'' = J} (a_I \otimes \omega_I) \otimes (a_{J'} \otimes \omega_{J'}) \otimes (a_{J''} \otimes \omega_{J''})
\end{align*}

Summing over all partitions $I \sqcup J = [0,n]$:
\[(\text{id} \otimes \Delta) \circ \Delta = \sum_{I \sqcup J' \sqcup J'' = [0,n]} (a_I \otimes \omega_I) \otimes (a_{J'} \otimes \omega_{J'}) \otimes (a_{J''} \otimes \omega_{J''})\]

\subsection*{Step 4: comparison}

\emph{LHS.} Sum over ordered partitions $(I', I'', J)$ with $I' \sqcup I'' \sqcup J = [0,n]$

\emph{RHS.} Sum over ordered partitions $(I, J', J'')$ with $I \sqcup J' \sqcup J'' = [0,n]$

These are the same set of ordered triples, in different notation.

Relabeling $I' \to K_1$, $I'' \to K_2$, $J \to K_3$ on LHS and $I \to K_1$, $J' \to K_2$, $J'' \to K_3$ on RHS:

Both sides equal:
\[\sum_{K_1 \sqcup K_2 \sqcup K_3 = [0,n]} (a_{K_1} \otimes \omega_{K_1}) \otimes (a_{K_2} \otimes \omega_{K_2}) \otimes (a_{K_3} \otimes \omega_{K_3})\]

Therefore: $(\Delta \otimes \text{id}) \circ \Delta = (\text{id} \otimes \Delta) \circ \Delta$.
\end{proof}

\begin{theorem}[Counit axioms; \ClaimStatusProvedHere]\label{thm:counit-axioms}
The counit $\epsilon: \bar{B}_n(\mathcal{A}) \to \mathbb{C}$ satisfies:
\begin{enumerate}
\item \emph{Left counit:} $(\epsilon \otimes \text{id}) \circ \Delta = \text{id}$
\item \emph{Right counit:} $(\text{id} \otimes \epsilon) \circ \Delta = \text{id}$
\end{enumerate}
\end{theorem}

\begin{proof}

The counit $\epsilon$ is:
\[\epsilon(a_0 \otimes \cdots \otimes a_n \otimes \omega) =
\begin{cases}
\langle a_0, 1 \rangle & n = 0 \\
0 & n > 0
\end{cases}\]

\subsection*{Left counit axiom}

For $(a_0 \otimes \cdots \otimes a_n \otimes \omega) \in \bar{B}_n(\mathcal{A})$:
\begin{align*}
&(\epsilon \otimes \text{id})(\Delta(a_0 \otimes \cdots \otimes a_n \otimes \omega)) \\
&= (\epsilon \otimes \text{id})\left(\sum_{I \sqcup J = [0,n]} (a_I \otimes \omega_I) \otimes (a_J \otimes \omega_J)\right) \\
&= \sum_{I \sqcup J = [0,n]} \epsilon(a_I \otimes \omega_I) \cdot (a_J \otimes \omega_J)
\end{align*}

Now $\epsilon(a_I \otimes \omega_I) = 0$ unless $|I| = 0$ (i.e., $I = \emptyset$).

When $I = \emptyset$, we have $J = [0,n]$ and:
\[\epsilon(1 \otimes \omega_{\emptyset}) \cdot (a_0 \otimes \cdots \otimes a_n \otimes \omega) = 1 \cdot (a_0 \otimes \cdots \otimes a_n \otimes \omega)\]

Therefore:
\[(\epsilon \otimes \text{id}) \circ \Delta = \text{id}\]

\subsection*{Right counit axiom}

Similarly:
\begin{align*}
&(\text{id} \otimes \epsilon)(\Delta(a_0 \otimes \cdots \otimes a_n \otimes \omega)) \\
&= \sum_{I \sqcup J = [0,n]} (a_I \otimes \omega_I) \cdot \epsilon(a_J \otimes \omega_J)
\end{align*}

$\epsilon(a_J \otimes \omega_J) = 0$ unless $|J| = 0$ (i.e., $J = \emptyset$).

When $J = \emptyset$, we have $I = [0,n]$ and:
\[(a_0 \otimes \cdots \otimes a_n \otimes \omega) \cdot \epsilon(1 \otimes \omega_{\emptyset}) = (a_0 \otimes \cdots \otimes a_n \otimes \omega) \cdot 1\]

Therefore:
\[(\text{id} \otimes \epsilon) \circ \Delta = \text{id}\]
\end{proof}

\begin{corollary}[Bar complex is DG-coalgebra; \ClaimStatusProvedHere]\label{cor:bar-is-dgcoalg}
The bar complex $\bar{B}^{\text{geom}}(\mathcal{A})$ with:
\begin{itemize}
\item Differential $d = d_{\text{int}} + d_{\text{res}} + d_{\text{dR}}$ (satisfying $d^2 = 0$)
\item Coproduct $\Delta$ (coassociative)
\item Counit $\epsilon$ (satisfying counit axioms)
\end{itemize}
is a differential graded coalgebra.
\end{corollary}
\begin{proof}
This assembles Theorem~\ref{thm:bar-nilpotency-complete} ($d^2 = 0$), Theorem~\ref{thm:coassociativity-complete} (coassociativity of $\Delta$), and Theorem~\ref{thm:counit-axioms} (counit axioms).  The compatibility $d \circ \Delta = \Delta \circ d$ is Theorem~\ref{thm:bar-coalgebra}.
\end{proof}

\begin{remark}[Geometric meaning of coassociativity]\label{rem:coassoc-geometric}
Coassociativity says the order of splitting does not matter: $(\Delta \otimes \text{id}) \circ \Delta$ (split, then split left) equals $(\text{id} \otimes \Delta) \circ \Delta$ (split, then split right).  Geometrically, corners of $\overline{C}_n(X)$ where multiple divisors intersect can be approached from different directions, giving consistent boundary data.
\end{remark}

\begin{theorem}[Differential is coderivation; \ClaimStatusProvedHere]\label{thm:diff-is-coderivation}
The differential $d$ on $\bar{B}(\mathcal{A})$ is a coderivation:
\[\Delta \circ d = (d \otimes \text{id} + \text{id} \otimes d) \circ \Delta\]
\end{theorem}

\begin{proof}
The coderivation identity $\Delta \circ d = (d \otimes \mathrm{id} + \mathrm{id} \otimes d) \circ \Delta$ is verified for each component of $d = d_{\mathrm{int}} + d_{\mathrm{res}} + d_{\mathrm{dR}}$ separately.

For $d_{\mathrm{int}}$: the internal differential acts on each tensor factor $\phi_i$ independently, and the deconcatenation coproduct $\Delta([a_1|\cdots|a_n]) = \sum_{i=0}^{n}[a_1|\cdots|a_i] \otimes [a_{i+1}|\cdots|a_n]$ splits the tensor factors.  The Leibniz rule $\Delta \circ d_{\mathrm{int}} = (d_{\mathrm{int}} \otimes \mathrm{id} + \mathrm{id} \otimes d_{\mathrm{int}}) \circ \Delta$ follows because $d_{\mathrm{int}}$ acts within each factor and commutes with the splitting.

For $d_{\mathrm{res}}$: the residue at $D_{ij}$ (collision of points $i$ and $j$) produces a term in bar degree $n-1$.  The coproduct restricts to boundary strata: $\Delta|_{D_{ij}}$ splits the remaining points into two groups, and the residue extraction commutes with this splitting because the divisor $D_{ij}$ lies entirely within the factor containing both $i$ and $j$.

For $d_{\mathrm{dR}}$: the exterior derivative satisfies $d_{\mathrm{dR}}(\omega_I \wedge \omega_J) = d_{\mathrm{dR}}\omega_I \wedge \omega_J + (-1)^{|\omega_I|}\omega_I \wedge d_{\mathrm{dR}}\omega_J$, which is the Leibniz rule with respect to the K\"unneth decomposition $\Omega^*(C_{n+1}(X)) \cong \bigoplus_{I \sqcup J} \Omega^*(C_{|I|}(X)) \otimes \Omega^*(C_{|J|}(X))$ used by $\Delta$.

This is the standard coderivation property for bar differentials; see~\cite{LV12}, Proposition~2.2.1 for the algebraic version.
\end{proof}

\begin{definition}[Genus-graded geometric bar complex]\label{def:geom-bar}
For a chiral algebra $\mathcal{A}$ on a Riemann surface $\Sigma_g$ of genus $g$, the \emph{genus-graded geometric bar complex} is the bigraded complex:
\[
\bar{B}^{(g)}_{p,q}(\mathcal{A}) = \Gamma\left(\overline{C}_{p+1}(\Sigma_g), j_*j^*\mathcal{A}^{\boxtimes(p+1)} \otimes \Omega^q_{\overline{C}_{p+1}(\Sigma_g)}(\log D^{(g)}) \otimes \text{or}_{p+1}^{(g)}\right)
\]
where:
\begin{itemize}
\item $\overline{C}_{p+1}(\Sigma_g)$ is the Fulton--MacPherson compactification at genus $g$
\item $D^{(g)} = \overline{C}_{p+1}(\Sigma_g) \setminus C_{p+1}(\Sigma_g)$ is the boundary divisor with genus-dependent stratification
\item $j: C_{p+1}(\Sigma_g) \hookrightarrow \overline{C}_{p+1}(\Sigma_g)$ is the open inclusion
\item $\Omega^q_{\overline{C}_{p+1}(\Sigma_g)}(\log D^{(g)})$ includes logarithmic forms and period integrals
\item $\text{or}_{p+1}^{(g)}$ is the genus-graded orientation bundle
\end{itemize}

The total bar complex is:
\[\bar{B}(\mathcal{A}) = \bigoplus_{g=0}^{\infty} \bar{B}^{(g)}(\mathcal{A})\]
\end{definition}
 
\begin{remark}[Orientation bundle]
The orientation bundle $\text{or}_{p+1}^{(g)}$ is necessary because configuration spaces are not naturally 
oriented at each genus. It is the determinant line of $T_{C_{p+1}(\Sigma_g)}$ with genus-dependent corrections, ensuring that our differential squares to zero across all genera and maintains modular covariance.
\end{remark}
 
\subsection{The differential -- detailed components}

The three-component decomposition $d = d_{\text{internal}} + d_{\text{residue}} + d_{\text{form}}$
of Definition~\ref{def:bar-differential-complete} is now expanded at genus~$g$.
 
\subsubsection{Internal differential}
 
\begin{definition}[Internal differential]
For $\alpha = \alpha_1 \otimes \cdots \otimes \alpha_{n+1} \otimes \omega \otimes \theta \in 
\bar{B}^{n,q}_{\text{geom}}(\mathcal{A})$ where $\theta \in \text{or}_{n+1}$:
\[
d_{\text{int}}(\alpha) = \sum_{i=1}^{n+1} (-1)^{|\alpha_1| + \cdots + |\alpha_{i-1}|} 
\alpha_1 \otimes \cdots \otimes d_{\mathcal{A}}(\alpha_i) \otimes \cdots \otimes \alpha_{n+1} \otimes \omega \otimes \theta
\]
where $d_{\mathcal{A}}$ is the internal differential on $\mathcal{A}$ (if present) and $|\alpha_i|$ denotes 
the cohomological degree.
\end{definition}
 
\subsubsection{Factorization differential}
 
\begin{definition}[Factorization differential]\label{def:diff-fact}
   The factorization differential encodes the chiral algebra structure:
   \[
   d_{\text{fact}} = \sum_{1 \leq i < j \leq n+1} (-1)^{\sigma(i,j)} \text{Res}_{D_{ij}} \left(\mu_{ij} \otimes (\eta_{ij} \wedge -)\right)
   \]
   where the sign is:
   \[\sigma(i,j) = i + j + \left(\sum_{k=1}^{i-1} |\alpha_k|\right) \cdot |\eta_{ij}|\]
   (Here $|\alpha_k|$ denotes the cohomological degree of the $k$-th element and $|\eta_{ij}| = 1$ for the logarithmic 1-form.)
   
   \emph{Geometric meaning.} This extracts the ``color'' $C_{ij}^k$ from the ``composite light'' of $\mathcal{A}$:
   \begin{center}
   \begin{tikzcd}
   \phi_i \otimes \phi_j \otimes \eta_{ij} \arrow[r, "d_{\text{fact}}"] & 
   \text{Res}_{D_{ij}}[\text{OPE}(\phi_i, \phi_j)] = \sum_k C_{ij}^k \phi_k
   \end{tikzcd}
   \end{center}
   
   Each residue reveals one structure coefficient, with the totality forming the complete ``spectrum.''
   
   This accounts for:
   \begin{itemize}
   \item Koszul sign from moving $\eta_{ij}$ past the fields $\alpha_k$
   \item Orientation of the divisor $D_{ij}$  
   \item Parity of the permutation after collision
   \end{itemize}
   \end{definition}
   
   \begin{lemma}[Orientation convention; \ClaimStatusProvedHere]\label{lem:orientation}
   Fix orientations on boundary divisors by:
   \begin{enumerate}
   \item For $D_{ij}$ where $z_i = z_j$:
      \[\text{or}_{D_{ij}} = dz_1 \wedge \cdots \wedge \widehat{dz_i} \wedge \cdots \wedge dz_{n+1}\]
      (omit $dz_i$, keep others including $dz_j$)
      
   \item For codimension-2 strata $D_{ijk} = D_{ij} \cap D_{jk}$:
      \[\text{or}_{D_{ijk}} = \text{or}_{D_{ij}} \wedge \text{or}_{D_{jk}}\]
      
   \item This implies the relation:
      \[\text{or}_{D_{ijk}} = -\text{or}_{D_{ik}} \wedge \text{or}_{D_{jk}} = \text{or}_{D_{jk}} \wedge \text{or}_{D_{ik}}\]
   \end{enumerate}
   
   These choices ensure $\partial^2 = 0$ for the boundary operator on $\overline{C}_{n+1}(X)$.
   \end{lemma}
   
   \begin{proof}
   The FM compactification $\overline{C}_{n+1}(X)$ is constructed by iterated real blow-up along diagonals (\cite{FM94}, \S2).  After blow-up, each codimension-1 boundary stratum $D_S$ (indexed by subsets $S \subset [n+1]$ with $|S| \geq 2$) is a smooth divisor, and distinct divisors $D_S, D_T$ meet transversally when $S \subset T$ or $T \subset S$ (nested), and are disjoint otherwise.  A codimension-2 stratum therefore arises as $D_S \cap D_T$ where $S \subsetneq T$ (a two-step degeneration), and the two orderings of the iterated boundary (first collapse $S$, then collapse $T/S$, versus directly collapsing $T$ and then refining to $S$) yield opposite orientations by the antisymmetry of the normal bundle orientations (Corollary~\ref{cor:residues-anticommute}).
   \end{proof}
   
   \begin{remark}[Significance of signs]
   The sign conventions are forced by $d^2 = 0$, following Kontsevich's principle: ``signs should be determined by geometry, not combinatorics.''
   \end{remark}
   
   \begin{lemma}[Residue properties; \ClaimStatusProvedHere]
   \label{lem:residue-properties}
   The residue operation satisfies:
   \begin{enumerate}
   \item $\text{Res}_{D_{ij}}^2 = 0$ (extracting residue lowers pole order)
   \item For disjoint pairs: $\text{Res}_{D_{ij}} \circ \text{Res}_{D_{k\ell}} = -\text{Res}_{D_{k\ell}} \circ \text{Res}_{D_{ij}}$
   \item For overlapping pairs with $j = k$: contributions combine via Jacobi identity
   \end{enumerate}
   \end{lemma}
   
   \begin{proof}
   Part~(1): A section $\omega \in \Omega^*_{\log}(\overline{C}_{n+1}(X))$ has at most a simple pole along $D_{ij}$.  In a local coordinate $u$ with $D_{ij} = \{u = 0\}$, write
   $\omega = f(u)\,d\log u + g(u)\,(\text{terms regular in }u)$
   where $f(0) = \mathrm{Res}_{D_{ij}}\omega$.  The residue $\mathrm{Res}_{D_{ij}}\omega = f(0)$ is a section on $D_{ij}$ with no pole along $D_{ij}$, so $\mathrm{Res}_{D_{ij}}^2\omega = \mathrm{Res}_{D_{ij}}(f(0)) = 0$.

   Part~(2): This is Corollary~\ref{cor:residues-anticommute}: for disjoint index pairs, the divisors $D_{ij}$ and $D_{k\ell}$ are transverse, and the anticommutativity follows from the antisymmetry of $d\log u \wedge d\log v$.

   Part~(3): For overlapping pairs with $j = k$, three codimension-1 strata $D_{ij}$, $D_{jk}$, and $D_{ik}$ meet at the triple collision stratum $D_{ijk}$.  The sum of iterated residues:
   \[
   \mathrm{Res}_{D_{jk}} \circ \mathrm{Res}_{D_{ij}} + \mathrm{Res}_{D_{ij}} \circ \mathrm{Res}_{D_{jk}} + \mathrm{Res}_{D_{ik}} \circ \mathrm{Res}_{D_{ij}}
   \]
   vanishes by the associativity of the chiral product, as verified in Case~(ii) of Theorem~\ref{thm:bar-nilpotency-complete}.
   \end{proof}
 
\begin{lemma}[Well-definedness of residue; \ClaimStatusProvedHere]
\label{lem:residue-well-defined}
The residue $\text{Res}_{D_{ij}}$ is well-defined on sections with logarithmic poles and satisfies:
\[
\text{Res}_{D_{ij}} \circ \text{Res}_{D_{k\ell}} = -\text{Res}_{D_{k\ell}} \circ \text{Res}_{D_{ij}}
\]
when $\{i,j\} \cap \{k,\ell\} = \emptyset$, and
\[
\text{Res}_{D_{ij}} \circ \text{Res}_{D_{ij}} = 0
\]
\end{lemma}
 
\begin{proof}
For anticommutativity: when $\{i,j\} \cap \{k,\ell\} = \emptyset$, the divisors $D_{ij}$ and $D_{k\ell}$ are transverse, and the result is Corollary~\ref{cor:residues-anticommute}.

For idempotency: in a local coordinate $u$ with $D_{ij} = \{u = 0\}$, any section $\omega \in \Omega^*_{\log}$ has the form $\omega = f\,d\log u + g$ where $g$ is regular along $D_{ij}$.  Then $\mathrm{Res}_{D_{ij}}\omega = f|_{u=0}$, which is regular along $D_{ij}$ (no $d\log u$ term), so $\mathrm{Res}_{D_{ij}}(f|_{u=0}) = 0$.
\end{proof}
 
\subsubsection{Configuration differential}
 
\begin{definition}[Configuration differential]
   The configuration differential is the de Rham differential on forms:
   \[d_{\text{config}} = d_{\text{config}}^{\text{dR}} + d_{\text{config}}^{\text{Lie*}}\]
   where the de~Rham component $d_{\text{config}}^{\text{dR}} = \text{id}_{\mathcal{A}^{\boxtimes(n+1)}} \otimes d_{\text{dR}} \otimes \text{id}_{\text{or}}$ acts on the differential forms, and the Lie$^*$ component $d_{\text{config}}^{\text{Lie*}} = \sum_{I \subset [n+1]} (-1)^{\epsilon(I)} d_{\text{Lie}}^{(I)} \otimes \text{id}_{\Omega^*}$ acts via the Lie$^*$ algebra structure (when present).
   
   For general chiral algebras without Lie* structure, $d_{\text{config}}^{\text{Lie*}} = 0$.
   \end{definition}
   
\begin{remark}[Geometric meaning]
   The configuration differential captures how $\mathcal{A}$ varies over configuration space: $d_{\text{dR}}$ measures variation of insertion points, $d_{\text{Lie*}}$ encodes infinitesimal symmetries.  This parallels the Cartan model for equivariant cohomology.
   \end{remark}

\subsection{Explicit residue computations}\label{sec:residue-calculus}

\begin{remark}[Sign conventions: comparison with Loday--Vallette]\label{rem:LV-signs}
Our sign conventions for the bar construction follow the geometric approach, which differs slightly from the operadic conventions in Loday--Vallette~\cite{LV12}.

The differences are as follows.
\begin{enumerate}
\item \emph{Koszul sign rule}: We use the \emph{geometric} Koszul rule where moving a differential form of degree $p$ past an operator of degree $q$ introduces $(-1)^{pq}$.

\item \emph{Residue orientation}: Our residues include an orientation factor from the normal bundle to collision divisors. This introduces signs when collision divisors intersect.

\item \emph{Suspension}: Loday--Vallette use operadic suspension $s: V \to sV$ with $|s| = 1$. We work with geometric forms directly, so suspension is implicit in the degree shift of $\Omega^n(\log D)$.
\end{enumerate}

\emph{Translation between conventions.}
\begin{center}
\begin{tabular}{|>{\raggedright\arraybackslash}p{0.43\textwidth}|>{\raggedright\arraybackslash}p{0.43\textwidth}|}
\hline
\textbf{Loday--Vallette (Operadic)} & \textbf{Ours (Geometric)} \\
\hline
$d_{op}(s a_1 \otimes \cdots \otimes s a_n)$ & $d_{geom}(a_1 \otimes \cdots \otimes a_n \otimes \omega_n)$ \\
Sign: $(-1)^{|a_1| + \cdots + |a_{i-1}|}$ & Sign: $(-1)^{\epsilon_i}$ (from form degree) \\
Suspension degree $|s a_i| = |a_i| + 1$ & Form degree $|\omega| = n$ \\
\hline
\end{tabular}
\end{center}

The two conventions agree up to an overall normalization constant (which can be absorbed into the definition of the pairing).

The nine-term proof of $d^2 = 0$ (Theorem~\ref{thm:bar-nilpotency-complete}) uses geometric signs throughout. Translating to operadic conventions via the dictionary above preserves $d^2 = 0$.
\end{remark}

\begin{theorem}[Geometric bar \texorpdfstring{$=$}{=} operadic bar; \ClaimStatusProvedHere]
\label{thm:geometric-equals-operadic-bar}
\index{geometric equals operadic bar}
\index{bar construction!algebraic}
\index{twisting morphism!chiral}
Let $\mathcal{P}^{\mathrm{ch}}$ be a chiral operad on $X$ (either
$\chirCom$ or $\chirAss$) and let $\mathcal{A}$ be an augmented
$\mathcal{P}^{\mathrm{ch}}$-algebra.  Then the geometric bar complex
$\bar{B}_{\mathrm{geom}}(\mathcal{A})$
(Definition~\ref{def:geometric-bar}) is naturally quasi-isomorphic
to the operadic bar construction
$B_{\mathcal{P}^{\mathrm{ch}}}(\mathcal{A})$ in the sense of
\cite[\S6.5]{LV12}:
\[
\bar{B}_{\mathrm{geom}}(\mathcal{A})
\;\xrightarrow{\;\sim\;}\;
B_{\mathcal{P}^{\mathrm{ch}}}(\mathcal{A}).
\]
The quasi-isomorphism is natural in $\mathcal{A}$ and compatible
with the coalgebra structures on both sides.
\end{theorem}

\begin{proof}
The operadic bar construction
$B_{\mathcal{P}}(\mathcal{A}) =
(\mathcal{P}^{!,c} \circ \bar{\mathcal{A}}, d_{\bar{B}})$
is a cofree $\mathcal{P}^!$-coalgebra on the augmentation ideal
$\bar{\mathcal{A}} = \ker(\varepsilon)$, with differential $d_{\bar{B}}$
encoding the algebra structure of $\mathcal{A}$ via the twisting
morphism $\kappa: \mathcal{P}^{!,c} \to \mathcal{P}$
\cite[Theorem~6.5.7]{LV12}.

\emph{Step 1} (Geometric realization of $\mathcal{P}^{!,c}$).
For $\mathcal{P} = \operatorname{Com}$ (the $\Einf$-chiral case),
$\mathcal{P}^{!,c} = \operatorname{Lie}^c$, and the cooperad
$\operatorname{Lie}^c(n)$ is computed by the cohomology of the
Fulton--MacPherson compactification $\overline{C}_n(X)$: the Arnold
relations on $H^*(\overline{C}_n)$ generate the Lie cooperad.
For $\mathcal{P} = \operatorname{Ass}$,
$\mathcal{P}^{!,c} = \operatorname{Ass}^c$ (the associative
cooperad), realized by ordered configurations.

\emph{Step 2} (Identification of differentials).
The operadic differential $d_{\bar{B}}$ decomposes into $d_1$ (the cooperadic cocomposition $\mathcal{P}^{!,c}(n)
\xrightarrow{\Delta} \mathcal{P}^{!,c}(k)
\otimes \mathcal{P}^{!,c}(n_1) \otimes \cdots
\otimes \mathcal{P}^{!,c}(n_k)$) and $d_2$ (the twisting morphism applied to pairs of consecutive inputs).
Under the geometric realization, $d_1$ corresponds to the de~Rham
differential $d_{\mathrm{dR}}$ on $\Omega^*(\log D)$ (which detects
the codimension-one boundary strata of $\overline{C}_n(X)$), and
$d_2$ corresponds to the residue differential $d_{\mathrm{res}}$
(which extracts OPE data at collision divisors).  The sign
comparison of Remark~\ref{rem:LV-signs} shows these agree up to
the suspension isomorphism
$s\bar{\mathcal{A}} \cong \bar{\mathcal{A}} \otimes
\Omega^1(\log D)|_{\text{codim-1}}$.

\emph{Step 3} (Quasi-isomorphism).
The comparison map sends a geometric bar element
$a_1 \otimes \cdots \otimes a_n \otimes \omega
\in \bar{B}_{\mathrm{geom}}^n(\mathcal{A})$
to the operadic bar element
$[sa_1 | \cdots | sa_n] \in B_{\mathcal{P}}(\mathcal{A})_n$
by evaluating the logarithmic form $\omega$ at the fundamental class
of the fiber.  This evaluation is a chain map by Stokes's theorem
(boundary terms match the residue differential by Step~2).
It is a quasi-isomorphism by the logarithmic comparison theorem:
the complex $\Omega^*_{\overline{C}_{n+1}(X)}(\log D)$ computes
$H^*(C_{n+1}(X); \mathbb{C})$ (the cohomology of the open configuration
space), and the operadic bar differential encodes precisely the
combinatorics of the boundary divisor stratification of
$\overline{C}_{n+1}(X)$; both are controlled by the operad structure
on $\{C_{n+1}(X)\}_{n \geq 0}$
(cf.\ \cite[Theorem~3.7.4]{BD04}, \cite[Theorem~5.1]{Get95}).
\end{proof}

\begin{theorem}[Residue formula; \ClaimStatusProvedHere]\label{thm:residue-formula}
\index{residue!iterated}
Following Beilinson--Drinfeld \cite[§3.7.4, p.228]{BD04}, 
let $\mathcal{A}$ be generated by fields $\phi_\alpha(z)$ with conformal weights $h_\alpha$ and OPE:

\footnote{The distributional nature of operator products requires care in defining 
products of distributions. We follow Hörmander's theory of wavefront sets: the OPE 
is well-defined when wavefront sets are in general position. See Hörmander, 
\textit{Analysis of Linear Partial Differential Operators I}, Theorem 8.2.10, or 
Costello--Gwilliam Vol. 1, \S2.4 for the QFT perspective.}

\[
\phi_\alpha(z)\phi_\beta(w) \sim \sum_{\gamma} \sum_{n=0}^{N_{\alpha\beta}} 
\frac{C^{\gamma,n}_{\alpha\beta} \partial^n\phi_\gamma(w)}{(z-w)^{h_\alpha + h_\beta - h_\gamma - n}}
+ \text{regular}
\]
where the sum is finite (quasi-finite OPE). Then:
\[
\text{Res}_{D_{ij}}[\phi_{\alpha_1}(z_1) \otimes \cdots \otimes \phi_{\alpha_{n+1}}(z_{n+1}) 
\otimes \eta_{i_1j_1} \wedge \cdots \wedge \eta_{i_kj_k}]
\]
equals:
\begin{itemize}
\item If $(i,j) \notin \{(i_r, j_r)\}_{r=1}^k$: zero (no pole along $D_{ij}$)
\item If $(i,j) = (i_r, j_r)$ for unique $r$ and $h_{\alpha_i} + h_{\alpha_j} - h_\gamma - n = 1$:
\[
(-1)^r C^{\gamma,n}_{\alpha_i\alpha_j} \phi_{\alpha_1} \otimes \cdots \otimes \partial^n\phi_\gamma \otimes \cdots 
\otimes \widehat{\phi_{\alpha_j}} \otimes \cdots \otimes \eta_{i_1j_1} \wedge \cdots \wedge \widehat{\eta_{ij}} \wedge \cdots
\]
where the hat denotes omission
\item Otherwise: zero (wrong pole order)
\end{itemize}

The \emph{criticality condition} $h_{\alpha_i} + h_{\alpha_j} - h_\gamma - n = 1$ is essential: only simple poles contribute to the residue (BD~\cite[\S3.7.4]{BD04}).
\end{theorem}
 
\begin{proof}
Near $D_{ij}$, we use blow-up coordinates $(u, \epsilon, \theta)$ where:
\[
z_i = u + \frac{\epsilon}{2}e^{i\theta}, \quad z_j = u - \frac{\epsilon}{2}e^{i\theta}
\]
The logarithmic form becomes:
\[
\eta_{ij} = d\log(\epsilon e^{i\theta}) = d\log\epsilon + id\theta
\]
The OPE gives:
\[
\phi_{\alpha_i}(z_i)\phi_{\alpha_j}(z_j) = \sum_{\gamma,n} 
\frac{C^{\gamma,n}_{\alpha_i\alpha_j} \partial^n\phi_\gamma(u)}{(\epsilon e^{i\theta})^{h_{\alpha_i} + h_{\alpha_j} - h_\gamma - n}}
+ O(\epsilon^0)
\]
The residue $\text{Res}_{D_{ij}}$ extracts the coefficient of
$\frac{d\log\epsilon}{\epsilon}$, which is nonzero only when the pole
order equals~$1$, i.e., when
$h_{\alpha_i} + h_{\alpha_j} - h_\gamma - n = 1$. This is the 
\emph{criticality condition} for the residue pairing. The sign $(-1)^r$ comes from 
moving $\eta_{ij}$ past $r-1$ other 1-forms via the Koszul rule for graded
commutativity.
\end{proof}
 
\subsection{Uniqueness and functoriality}
 
\begin{theorem}[Uniqueness and functoriality; \ClaimStatusProvedHere]\label{thm:bar-uniqueness-functoriality}
The geometric bar construction is the unique functor 
\[\bar{B}_{geom}: \text{ChirAlg}_X \to \text{dgCoalg}\]
satisfying:
\begin{enumerate}
\item \emph{Locality:} For $j: U \hookrightarrow X$ open, $j^*\bar{B}_{geom}(\mathcal{A}) \cong \bar{B}_{geom}(j^*\mathcal{A})$
\item \emph{External product:} $\bar{B}_{geom}(\mathcal{A} \boxtimes \mathcal{B}) \cong \bar{B}_{geom}(\mathcal{A}) \boxtimes \bar{B}_{geom}(\mathcal{B})$
\item \emph{Normalization:} $\bar{B}_{geom}(\mathcal{O}_X) = \Omega^*(\overline{\mathcal{C}}_{*+1}(X))$
\end{enumerate}
up to unique natural isomorphism.

It defines a functor from chiral algebras to filtered conilpotent chiral coalgebras, with essential image the coalgebras having logarithmic coderivations supported on collision divisors.
\end{theorem}

 
\begin{definition}[Conilpotent chiral coalgebra]
A chiral coalgebra $C$ is \emph{filtered conilpotent} if the iterated comultiplication 
$\Delta^{(n)} : C \to C^{\otimes(n+1)}$ satisfies: For each $c \in C$, there exists 
$N$ such that $\Delta^{(n)}(c) = 0$ for all $n \geq N$. This ensures the cobar 
construction $\Omega^{\text{ch}}(C)$ is well-defined without completion.
\end{definition}



\begin{proof}
\emph{Step 1: Existence.} We verify each axiom explicitly:
\begin{itemize}
\item \emph{Locality:} For $j: U \hookrightarrow X$ open,
we have $C_n(U) = j^{-1}(C_n(X))$.
The maximal extension $j_*j^*$ commutes with sections over
configuration spaces:
\begin{align*}
j^*\bar{B}_{\text{geom}}(A)
&= j^*\Gamma(\overline{C}_{n+1}(X), \cdots) \\
&= \Gamma(\overline{C}_{n+1}(U), \cdots)
= \bar{B}_{\text{geom}}(j^*A)
\end{align*}

\item \emph{External product:} For disjoint open subsets
$U_1, U_2 \subset X$, the identification
$C_n(U_1 \sqcup U_2) \cong
\bigsqcup_{k+l=n} C_k(U_1) \times C_l(U_2)$
induces a natural isomorphism
\[
\bar{B}_{\mathrm{geom}}(\mathcal{A}|_{U_1 \sqcup U_2})
\cong \bigoplus_{k+l=n}
\bar{B}_k(\mathcal{A}|_{U_1}) \otimes
\bar{B}_l(\mathcal{A}|_{U_2}),
\]
compatible with boundary stratifications.

\item \emph{Normalization:} For $A = \mathcal{O}_X$, there are no nontrivial OPEs, so 
$d_{\text{fact}} = 0$, and we are left with just the de Rham complex on configuration spaces.
\end{itemize}

\emph{Step 2: Uniqueness.} Let $F, G$ be two such functors. 

For the structure sheaf: By normalization, 
\[F(\mathcal{O}_X) = G(\mathcal{O}_X) = \Omega^*(\overline{\mathcal{C}}_{*+1}(X))\]

For free chiral algebra $\text{Free}_{ch}(V)$ on a vector bundle $V$:
The locality and external product axioms determine:
\[F(\text{Free}^{\text{ch}}(V)) \cong \text{Sym}^*(V[1]) \otimes \Omega^*(\overline{C}_{*+1}(X))\]
and similarly for $G$, giving canonical isomorphism $\eta_V: F(\text{Free}^{\text{ch}}(V)) \xrightarrow{\sim} G(\text{Free}^{\text{ch}}(V))$.


\begin{align}
F(\text{Free}_{ch}(V)) &= F(V^{\otimes_{ch} \bullet})\\
&\cong F(V)^{\otimes \bullet} \quad \text{(external product)}\\
&\cong (V[1] \otimes F(\mathcal{O}_X))^{\otimes \bullet} \quad \text{(locality)}\\
&\cong \text{Sym}^*(V[1]) \otimes \Omega^*(\overline{\mathcal{C}}_{*+1}(X))
\end{align}

Similarly for $G$, giving canonical isomorphism $\eta_{V}: F(\text{Free}_{ch}(V)) \xrightarrow{\sim} G(\text{Free}_{ch}(V))$.

For general $\mathcal{A} = \text{Free}_{ch}(V)/R$:
The relations $R$ determine boundaries via the same residue formulas in both $F(A)$ and $G(A)$:
\begin{itemize}
\item Each relation $r \in R$ maps to $d_{\text{fact}}(r)$ computed via residues
\item The residue formula is determined by the OPE structure
\item Locality ensures these agree on all affine charts
\end{itemize}

\emph{Step 3: Natural isomorphism.} 
For morphism $\phi: \mathcal{A} \to \mathcal{B}$, the diagram
\[
\begin{tikzcd}
F(\mathcal{A}) \arrow[r, "\eta_\mathcal{A}"] \arrow[d, "F(\phi)"] & G(\mathcal{A}) \arrow[d, "G(\phi)"]\\
F(\mathcal{B}) \arrow[r, "\eta_\mathcal{B}"] & G(\mathcal{B})
\end{tikzcd}
\]
commutes by construction of $\eta$ using universal properties.

\emph{Verification that relations map to boundaries}: Let $r \in R \subset \text{Free}^{\text{ch}}(V) \otimes \text{Free}^{\text{ch}}(V)$.
Under $F$, we have:
\[F(r) \in F(\text{Free}^{\text{ch}}(V) \otimes \text{Free}^{\text{ch}}(V)) = F(\text{Free}^{\text{ch}}(V))^{\otimes 2}\]
\[ = (V[1] \otimes \Omega^*(C_{*+1}(X)))^{\otimes 2}\]
The differential $d_F$ maps $r$ to the boundary because:
\[d_F(r) = d_{\text{fact}}(r) + d_{\text{config}}(r) + d_{\text{int}}(r)\]
where $d_{\text{fact}}$ implements the relation via residue extraction. Similarly for $G$.
The agreement $F(r) = G(r)$ in cohomology follows from the universal property
of free chiral algebras and the uniqueness of residue extraction.

\emph{Step 4: Uniqueness of isomorphism.}
Any other natural isomorphism $\eta': F \Rightarrow G$ must agree on $\mathcal{O}_X$ by normalization,
hence on free algebras by external product, hence on all algebras by locality.
\end{proof}

\subsection{Bar complex as chiral coalgebra}

\begin{theorem}[Bar complex is chiral; \ClaimStatusProvedHere]\label{thm:bar-chiral}
\index{factorization coalgebra|textbf}
The geometric bar complex $\bar{B}^{\text{ch}}(\mathcal{A})$ naturally carries the structure of a differential graded chiral coalgebra.
\end{theorem}

\begin{proof}
We construct the chiral coalgebra structure explicitly:

\emph{Comultiplication.} The map $\Delta: \bar{B}^{\text{ch}}(\mathcal{A}) \to \bar{B}^{\text{ch}}(\mathcal{A}) \otimes \bar{B}^{\text{ch}}(\mathcal{A})$ is induced by:
\[
\Delta: \overline{C}_{n+1}(X) \to \bigcup_{I \sqcup J = [n+1]} \overline{C}_{|I|}(X) \times \overline{C}_{|J|}(X)
\]
where the union is over ordered partitions with $0 \in I$. Explicitly:
\[
\Delta(\phi_0 \otimes \cdots \otimes \phi_n \otimes \omega) = \sum_{I \sqcup J} \pm \left(\bigotimes_{i \in I} \phi_i \otimes \omega|_I\right) \otimes \left(\bigotimes_{j \in J} \phi_j \otimes \omega|_J\right)
\]

\emph{Counit.} $\epsilon: \bar{B}^{\text{ch}}(\mathcal{A}) \to \mathbb{C}$ is given by projection onto degree 0:
\[
\epsilon(\phi_0 \otimes \cdots \otimes \phi_n \otimes \omega) = \begin{cases}
\int_X \phi_0 & \text{if } n = 0 \\
0 & \text{if } n > 0
\end{cases}
\]

\emph{Coassociativity.} Follows from the associativity of configuration space stratifications
(the stratification $\overline{C}_{n_1+n_2}(X) \supset C_{n_1}(X) \times C_{n_2}(X)$ is associative in the sense that iterated boundary extraction $(I_1, I_2, I_3) \mapsto (I_1 \mid I_2 \mid I_3)$ is independent of the order of extraction, by the transversality of the strata):
\[
(\Delta \otimes \text{id}) \circ \Delta = (\text{id} \otimes \Delta) \circ \Delta
\]

\emph{Compatibility with differential.} The comultiplication is a chain map:
\[
\Delta \circ d = (d \otimes \text{id} + \text{id} \otimes d) \circ \Delta
\]
This follows from the compatibility of residues with the stratification of configuration spaces
(the residue of $d\omega$ along a boundary stratum equals the residue of $\omega$ on the induced stratum, by the compatibility of the Leray residue with the boundary map in the long exact sequence of the pair).
\end{proof}

