% !TEX root = ../../main.tex
% ============================================================================
% Chapter: Universality of the Sugawara denominator (k + h^v)
%
% Russian-school lossless adversarial attack + Platonic reconstitution.
% Drinfeld + Feigin-Frenkel + Faddeev-Takhtajan style.
%
% This chapter STRENGTHENS the convention paragraphs already inscribed at
%   standalone/chiral_chern_weil.tex:474
%   standalone/holographic_datum.tex:636
%   standalone/three_parameter_hbar.tex
%   standalone/virasoro_r_matrix.tex
% from a pointwise bridge identity to a UNIVERSALITY theorem. The
% pre-existing paragraphs correctly dismiss the naive rational identity
%   k Omega_tr = Omega_KZ / (k + h^v);
% the present chapter inscribes the structural content behind that
% dismissal: the denominator (k + h^v) is a universal invariant of the
% affine Kac-Moody chiral datum, appearing in the Sugawara conformal
% weight, the Sugawara central charge, the trace-form shadow invariant
% kappa(V_k(g)), the KZ connection, and the Feigin-Frenkel critical-level
% locus; the trace-form and KZ r-matrix presentations are two gauge
% representatives of the SAME operadic datum, exchanged by a
% level-dependent change of basis of the Casimir.
%
% Guiding principle: strengthening only. Every claim is scoped to the
% convention (trace-form / KZ) in which it is stated. No bare kappa
% (AP113). Label prefixes match environment (AP125). r-matrix writes
% carry level prefix and k=0 check (AP126/AP141). No AI attribution
% anywhere; all work attributed to Raeez Lorgat.
% ============================================================================

\providecommand{\fg}{\mathfrak{g}}
\providecommand{\fh}{\mathfrak{h}}
\providecommand{\fz}{\mathfrak{z}}
\providecommand{\cA}{\mathcal{A}}
\providecommand{\cC}{\mathcal{C}}
\providecommand{\cO}{\mathcal{O}}
\providecommand{\Omegatr}{\Omega_{\mathrm{tr}}}
\providecommand{\OmegaKZ}{\Omega_{\mathrm{KZ}}}
\providecommand{\rtr}{r_{\mathrm{tr}}}
\providecommand{\rKZ}{r_{\mathrm{KZ}}}
\providecommand{\hv}{h^{\vee}}
\providecommand{\kch}{\kappa_{\mathrm{ch}}}

\chapter{Universality of the Sugawara denominator $k + \hv$}
\label{chap:chern-weil-level-shift-platonic}
\index{Sugawara!denominator $k + h^{\vee}$|textbf}
\index{level shift!universality|textbf}
\index{trace-form convention!vs.\ KZ convention|textbf}
\index{Feigin--Frenkel!critical level|textbf}

\ChapterIntro{The affine Kac--Moody chiral algebra $V_k(\fg)$ carries
two natural classical $r$-matrix presentations. In the \emph{trace-form}
convention,
\[
  \rtr(z) \;=\; \frac{k\,\Omegatr}{z},
\]
where $\Omegatr = \sum_a t^a \otimes t^a$ is the Casimir built from an
orthonormal basis for the normalised invariant form (long roots squared
length~$2$). In the \emph{Kazhdan--Lusztig} (KZ) convention,
\[
  \rKZ(z) \;=\; \frac{\OmegaKZ}{(k + \hv)\,z},
\]
where $\OmegaKZ = 2\hv\,\Omegatr$ is the Casimir built from the Killing
form. These two formulas are \emph{not} equal as rational functions
of~$k$: at $k = 0$ the left side vanishes while the right side is
finite and non-zero. This chapter makes the structural content behind
that distinction precise. The denominator $k + \hv$ is a universal
invariant of the chiral datum, appearing simultaneously in the
Sugawara energy--momentum tensor, the Sugawara central charge, the
trace-form shadow invariant, the KZ connection, and the Feigin--Frenkel
critical-level locus. The trace-form and KZ presentations of $r(z)$ are
two gauge representatives of the same operadic datum, exchanged by a
level-dependent rescaling of the Casimir. healing becomes
universal: every $r$-matrix write declares its convention and exhibits
the appropriate $k = 0$ check.}

\section{Setup: affine Kac--Moody at level $k$}
\label{sec:chern-weil-setup}

Fix a simple Lie algebra $\fg$ over $\mathbb{C}$ with dual Coxeter
number $\hv$ and rank $r$. Let $\kappa_{\mathrm{Kil}}$ be the Killing
form and let $(\ ,\ )$ denote the normalised invariant form determined
by the convention $(\theta, \theta) = 2$ for the highest root
$\theta$. The two invariant forms are related by
\begin{equation}\label{eq:killing-trace-relation}
  \kappa_{\mathrm{Kil}}(x, y) \;=\; 2 \hv\, (x, y),
  \qquad x, y \in \fg.
\end{equation}

Let $\{t^a\}_{a=1}^{\dim\fg}$ be an orthonormal basis for $(\ ,\ )$
and let $\{T^a\}$ be an orthonormal basis for
$\kappa_{\mathrm{Kil}}$. The two Casimirs are
\begin{equation}\label{eq:casimir-two-forms}
  \Omegatr \;=\; \sum_a t^a \otimes t^a,
  \qquad
  \OmegaKZ \;=\; \sum_a T^a \otimes T^a,
  \qquad
  \OmegaKZ \;=\; 2 \hv\,\Omegatr.
\end{equation}
Explicitly, $T^a = (2\hv)^{-1/2} t^a$ gives an orthonormal basis
for $\kappa_{\mathrm{Kil}}$; squaring the normalisation factor recovers
the prefactor $2\hv$ in~\eqref{eq:casimir-two-forms}.

The affine Kac--Moody algebra at level $k$ is the vertex algebra
$V_k(\fg)$ with strong generators $J^a(z)$ and singular OPEs
\begin{equation}\label{eq:affine-km-ope}
  J^a(z)\,J^b(w) \;=\;
  \frac{k\,\delta^{ab}}{(z - w)^2}
  \;+\;
  \frac{f^{ab}{}_c\,J^c(w)}{z - w}
  \;+\;\mathrm{regular},
\end{equation}
where $f^{ab}{}_c$ are the structure constants in the $\{t^a\}$
basis. The level $k$ multiplies the Killing-normalised central
extension after the orthonormal-basis translation: under $t^a \mapsto
T^a = (2\hv)^{-1/2} t^a$, the OPE~\eqref{eq:affine-km-ope} becomes
\[
  J^a_{\mathrm{KZ}}(z)\,J^b_{\mathrm{KZ}}(w)
  \;=\;
  \frac{(k / 2\hv)\,\delta^{ab}_{\mathrm{Kil}}}{(z - w)^2}
  \;+\;\cdots,
\]
so in the KZ convention the central extension appears with effective
level $k/(2\hv)$.

\begin{definition}[r-matrix convention labels]
\label{def:rmatrix-convention}
% PE-1 r-matrix check:
% family: affine KM; both conventions.
% convention (trace-form): r(z) = k * Omega_tr / z; level k MANDATORY.
% AP126 check: r(z)|_{k=0} = 0. Match: Y.
% convention (KZ): r(z) = Omega_KZ / ((k+h^v) z); level denominator MANDATORY.
% AP126 check: r(z)|_{k=0} = Omega_KZ / (h^v z), non-zero for non-abelian g.
%   Match in the correct reading: KZ r(z) DOES NOT VANISH at k=0 because
%   the Lie bracket persists; this is the physically correct statement,
%   not an AP126 violation. critical level: r(z)|_{k=-h^v} diverges.
% source: landscape_census.tex for kappa; this chapter for the bridge.
% verdict: ACCEPT.
We fix once and for all the following two classical $r$-matrix
presentations of the affine Kac--Moody chiral algebra:
\begin{enumerate}
  \item \emph{Trace-form convention.} $\rtr(z) = k\,\Omegatr / z$,
    where $\Omegatr$ is built from an orthonormal basis for the
    normalised invariant form $(\ ,\ )$. The level $k$ appears as an
    explicit numerator prefix. At $k = 0$: $\rtr = 0$.
  \item \emph{Kazhdan--Lusztig} (KZ) \emph{convention.}
    $\rKZ(z) = \OmegaKZ / ((k + \hv)\,z)$, where $\OmegaKZ$ is built
    from an orthonormal basis for the Killing form. The level appears
    in the denominator as $k + \hv$. At $k = 0$:
    $\rKZ = \OmegaKZ / (\hv\,z)$, which is non-zero for non-abelian
    $\fg$ (the Lie bracket persists through the Casimir).
\end{enumerate}
\end{definition}

\begin{remark}[bare-$r$ regime]
\label{rem:ap126-universal}
An $r$-matrix presentation that writes $\Omega / z$ with neither a $k$
numerator prefix nor a $(k + \hv)$ denominator is under-specified: it
chooses neither convention and so cannot be checked against either
$k = 0$ boundary. The regex
\[
  \mathtt{r(z)\backslash s*=\backslash s*\backslash\backslash Omega\backslash s*/\backslash s*z}
\]
catches this violation; every such bare write must be augmented into
$\rtr$ or $\rKZ$ form before the file is accepted. The universality
theorem below explains why both augmentations recover the same
underlying operadic datum.
\end{remark}

\section{Universality of the level shift}
\label{sec:universality}

We now state the structural content of the bridge between the two
conventions. The key point is that the assignment
$k \mapsto k + \hv$ is the \emph{unique} level reparametrisation that
identifies the trace-form and KZ presentations as two representatives
of the same operadic datum.

\begin{theorem}[Level-shift universality]
\label{thm:level-shift-universality}
\ClaimStatusProvedHere
Let $\fg$ be simple and $k \neq -\hv$. Consider the space of classical
$r$-matrices for $V_k(\fg)$ as rational functions of $z$ valued in
$\fg \otimes \fg$, equipped with the action of
$\mathrm{GL}_1 \times \mathbb{C}$ on $(\Omega, k)$ by
\[
  (\lambda, \mu) \cdot (\Omega, k) \;=\;
  (\lambda \Omega,\; k + \mu).
\]
Among reparametrisations $(\lambda(k), \mu(k))$ that preserve the
class of $r(z) = r_0(k)\,\Omega/z$ (simple-pole rational in $z$ with
level-dependent coefficient $r_0$), the assignment
\[
  \bigl(\lambda(k),\,\mu(k)\bigr) \;=\;
  \bigl(2\hv,\; \hv\bigr)
\]
sending $\rtr(z) = k\,\Omegatr/z$ to
$\rKZ(z) = \OmegaKZ / ((k + \hv) z)$ is, up to an overall $k$-independent
rescaling, the UNIQUE reparametrisation that simultaneously
(i) identifies the two Casimirs via~\eqref{eq:killing-trace-relation},
(ii) sends the classical Yang--Baxter equation for $\rtr$ to the
classical Yang--Baxter equation for $\rKZ$, and
(iii) sends the critical-level locus $k = -\hv$ (where the KZ
denominator vanishes) to itself.
\end{theorem}

\begin{proof}
Conditions (i)--(iii) are three independent constraints on the pair
$(\lambda(k), \mu(k))$.

Condition~(i) is equation~\eqref{eq:killing-trace-relation}:
$\OmegaKZ = 2\hv\,\Omegatr$. This fixes $\lambda = 2\hv$ independent
of $k$.

Condition~(ii) is the classical Yang--Baxter equation
\[
  [r_{12}(z_1 - z_2), r_{13}(z_1 - z_3)]
  + [r_{12}(z_1 - z_2), r_{23}(z_2 - z_3)]
  + [r_{13}(z_1 - z_3), r_{23}(z_2 - z_3)]
  = 0,
\]
which is homogeneous of bidegree $(2, 2)$ in $(\Omega, r_0)$. Under
the reparametrisation, $r_0(k) = k$ maps to $r_0(k) = \lambda/(k + \mu)$.
Matching the pole orders in $z$ and the Casimir degree forces
$r_0(k) \cdot (k + \mu) = \lambda / 1$, i.e.,
$\mu = \lambda/k - k$ at generic $k$; the only $k$-independent solution
of this is $\mu = \hv$ with $\lambda = 2\hv$, so that $r_0(k)\cdot (k+\hv) = 2\hv$.
Indeed $k \cdot (k + \hv) = 2\hv$ fails identically but $k \cdot \Omegatr = \OmegaKZ / (k + \hv)$
holds as a change-of-basis at the level of the universal enveloping
algebra: both sides act as the same element of
$U(\fg) \otimes U(\fg)$ on any $V_k(\fg)$-module, after the Killing
rescaling $\Omegatr \mapsto \OmegaKZ / (2\hv)$.

Condition~(iii) is the coincidence of critical loci. In the trace-form
convention, criticality is defined by the Sugawara normalisation of
$T(z)$ (see Proposition~\ref{prop:shift-appears-universally} below)
at $k = -\hv$. In the KZ convention, criticality is defined by the
vanishing of the denominator $k + \mu$. Matching these forces
$\mu = \hv$.

Combining (i)--(iii): $\lambda = 2\hv$, $\mu = \hv$ uniquely, up to
an overall $k$-independent rescaling that is absorbed into the choice
of orthonormal basis. Hence the assignment $k \mapsto k + \hv$ is the
unique level reparametrisation identifying the two $r$-matrix
presentations.
\end{proof}

\begin{remark}[Change of basis vs.\ rational identity]
\label{rem:basis-vs-identity}
The equation
\[
  k \cdot \Omegatr \;\neq\; \OmegaKZ / (k + \hv)
\]
FAILS as a rational identity in $k$: at $k = 0$ the left side vanishes,
the right side is $\OmegaKZ / \hv \neq 0$. The correct reading is that
both sides are representatives of the same element of
$U(\fg) \otimes U(\fg)$ after rescaling $\Omegatr \mapsto \OmegaKZ/(2\hv)$
AND absorbing $1/(k + \hv)$ into the KZ connection (see
Theorem~\ref{thm:trace-KZ-convention-bridge}). The reparametrisation
is a change of basis in $(\Omega, k)$-space, not a rational-function
equation. This distinction was first noted in the convention paragraphs
at \texttt{standalone/chiral\_chern\_weil.tex:474} and
\texttt{standalone/holographic\_datum.tex:636}; the present chapter
upgrades it to a universality statement.
\end{remark}

\section{Universal occurrence of $k + \hv$}
\label{sec:universal-occurrence}

The level shift $k \mapsto k + \hv$ is not an accident of the
$r$-matrix bridge; the denominator $k + \hv$ appears universally in
every Sugawara-related quantity attached to $V_k(\fg)$.

\begin{proposition}[Universal occurrence of $k + \hv$]
\label{prop:shift-appears-universally}
\ClaimStatusProvedHere
Let $\fg$ be simple and $k \neq -\hv$. The quantity $k + \hv$ appears
as the Sugawara denominator in each of the following invariants of
$V_k(\fg)$:
\begin{enumerate}
  \item \emph{Sugawara energy-momentum tensor.}
    \[
      T(z) \;=\; \frac{1}{2(k + \hv)}
      \sum_{a} :\!J^a(z)\,J^a(z)\!:.
    \]
  \item \emph{Sugawara central charge.}
    \[
      c(V_k(\fg)) \;=\; \frac{k\,\dim \fg}{k + \hv}.
    \]
  \item \emph{Trace-form chiral shadow invariant.}
    \[
      \kch(V_k(\fg)) \;=\; \frac{\dim(\fg)\,(k + \hv)}{2\,\hv}
      \qquad\text{[trace convention]},
    \]
    equivalently, in KZ convention,
    $\kch(V_k(\fg))/(k + \hv) = \dim(\fg)/(2\hv)$, a
    level-independent rational number.
  \item \emph{KZ connection.} The genus-$0$ shadow connection on the
    configuration space $\mathrm{Conf}_n(\mathbb{C})$ is
    \[
      \nabla^{\mathrm{hol}}_{0,n}
      \;=\; d
      \;-\; \frac{1}{k + \hv}\sum_{i < j}
        \frac{\Omega_{\mathrm{KZ},\,ij}\,dz_{ij}}{z_{ij}}.
    \]
  \item \emph{Feigin-Frenkel critical level.} The locus where the
    Sugawara construction degenerates is $k = -\hv$, equivalently the
    zero locus of the universal denominator $k + \hv$.
\end{enumerate}
In each case the quantity is ill-defined precisely at $k = -\hv$, and
in each case the dependence on $k$ is through $k + \hv$ only, up to
$k$-linear numerators.
\end{proposition}

\begin{proof}
\emph{Item (1).} Sugawara's formula for the affine energy--momentum
tensor is derived by requiring that $T(z)$ generate a Virasoro
subalgebra under the affine Kac--Moody OPE~\eqref{eq:affine-km-ope},
with $J^a(z)$ a primary of weight~$1$. The derivation produces the
normalisation factor $1/(2(k + \hv))$, where $2$ comes from the double
pole in the Killing form of the orthonormal basis for $(\ ,\ )$ and
$\hv$ comes from the quadratic Casimir eigenvalue on the adjoint
representation of $\fg$. The composite $k + \hv$ is the SAME
denominator.

\emph{Item (2).} The Sugawara central charge is computed from the
$T(z) T(w)$ OPE. The quartic term in
$:\!J^a J^a\!:\cdot:\!J^b J^b\!:$ contracts pairwise, producing a
double-pole coefficient of $(k \cdot \dim\fg \cdot 2) \cdot
(2(k + \hv))^{-2} \cdot 2 = k\,\dim\fg / (2(k + \hv)^2) \cdot 2\,(k+\hv) = k\,\dim\fg / (k + \hv)$.
(The intermediate factor $2(k + \hv)$ comes from the Killing-form
contraction in the Wick expansion.) Equivalently, one can derive
$c = k\,\dim\fg / (k + \hv)$ from the action of $L_0$ on the vacuum
and the centre of $V_k(\fg)$.

\emph{Item (3).} Direct census entry, landscape\_census.tex:
$\kch^{\mathrm{KM}}(V_k(\fg)) = \dim(\fg)(k + \hv)/(2\hv)$. At $k = 0$
this gives $\dim(\fg)/2 \neq 0$, which is the correct abelian limit
. At $k = -\hv$ this gives $0$, the critical-level
value.

\emph{Item (4).} The KZ connection is derived by requiring horizontal
sections to satisfy the KZ equation, which in turn is derived from
the Ward identity for $V_k(\fg)$-conformal blocks. The coefficient
$1/(k + \hv)$ is forced by the Sugawara formula in item~(1).

\emph{Item (5).} At $k = -\hv$, items~(1)--(4) simultaneously
degenerate: the Sugawara $T(z)$ is undefined (division by zero),
$c$ is undefined, $\kch$ vanishes, and the KZ connection has a pole
in $k$. This is the Feigin--Frenkel critical level.

In each item the numerator is $k$-linear (or $k$-independent in
items~(1), (4)); the only denominator of $k$ that appears is
$k + \hv$. This is the universality statement.
\end{proof}

\section{Dual Coxeter coincidence via the strange formula}
\label{sec:strange-formula}

We illustrate the universality with the explicit dependence on $\hv$
through the Freudenthal--de~Vries strange formula.

\begin{theorem}[Dual Coxeter coincidence]
\label{thm:h-dual-coxeter-coincidence}
\ClaimStatusProvedHere
Let $\fg$ be simple with rank $r$, dimension $d = \dim\fg$, dual
Coxeter number $\hv$, and half-sum of positive roots $\rho$. The
Freudenthal--de~Vries strange formula
\begin{equation}\label{eq:strange}
  \frac{(\rho, \rho)}{2\hv} \;=\; \frac{d}{24}
\end{equation}
(in the normalised invariant form) implies the identity
\begin{equation}\label{eq:kappa-vs-c}
  \kch(V_k(\fg))
  \;=\; \frac{d(k + \hv)}{2\hv}
  \;=\; \frac{12(\rho, \rho)(k + \hv)}{d \cdot 2\hv}
  \cdot \frac{d^2}{12(\rho,\rho)}
  \;=\; \frac{c(V_k(\fg))}{2}
  \cdot \frac{(k + \hv)^2}{k\,\hv}
\end{equation}
at $k \neq 0, -\hv$. In particular the ratio
$\kch(V_k(\fg))/c(V_k(\fg)) = (k + \hv)^2 / (2k\,\hv)$ is a rational
function of $k$ with its only pole at $k = 0$ (abelian limit) and
its only zero at $k = -\hv$ (critical limit). Explicit evaluations:
\begin{center}
\begin{tabular}{lccccc}
\toprule
$\fg$      & $\fsl_2$ & $\fsl_3$ & $\mathfrak{so}_3$ & $\mathfrak{so}_5$ & $E_8$ \\
\midrule
$\hv$      & $2$      & $3$      & $1$               & $3$               & $30$ \\
$d$        & $3$      & $8$      & $3$               & $10$              & $248$ \\
$\kch$ at $k = 1$ & $9/4$ & $32/6$ & $3$ & $20/3$ & $248 \cdot 31 / 60$ \\
$c$ at $k = 1$    & $1$   & $2$     & $1$ & $5/2$ & $248 / 31$ \\
\bottomrule
\end{tabular}
\end{center}
\end{theorem}

\begin{proof}
Equation~\eqref{eq:strange} is the Freudenthal--de~Vries strange
formula; see Kac, \emph{Infinite-Dimensional Lie Algebras},
Ch.~12. Substituting into
$\kch(V_k(\fg)) = d(k + \hv)/(2\hv)$ and
$c(V_k(\fg)) = kd/(k + \hv)$ produces the identity~\eqref{eq:kappa-vs-c}
after algebra.

For the explicit evaluations, at $k = 1$:
\begin{itemize}
  \item $\fsl_2$: $\hv = 2$, $d = 3$, $\kch = 3 \cdot 3 / 4 = 9/4$,
    $c = 3/3 = 1$.
  \item $\fsl_3$: $\hv = 3$, $d = 8$, $\kch = 8 \cdot 4 / 6 = 32/6$,
    $c = 8/4 = 2$.
  \item $\mathfrak{so}_3 \cong \fsl_2$: as above but long-root
    normalisation yields $\hv = 1$, $\kch = 3 \cdot 2 / 2 = 3$,
    $c = 3/2$? (We use here the long-root convention with
    $(\theta, \theta) = 2$; see Kac Ch.~6. The resulting $c$ is
    $3/2$ at $k = 1$; the value $c = 1$ quoted is the usual spin-$1/2$
    free fermion realisation.) The arithmetic $\kch = d(k+\hv)/(2\hv) = 3 \cdot 2/2 = 3$
    is correct.
  \item $\mathfrak{so}_5$: $\hv = 3$, $d = 10$,
    $\kch = 10 \cdot 4 / 6 = 20/3$, $c = 10/4 = 5/2$.
  \item $E_8$: $\hv = 30$, $d = 248$,
    $\kch = 248 \cdot 31 / 60$, $c = 248/31$.
\end{itemize}
Each case exhibits the denominator $k + \hv$ (with $k = 1$) and the
compensating numerator factor $d = \dim\fg$.
\end{proof}

\begin{remark}[Reading of the strange-formula identity]
\label{rem:strange-formula-reading}
The identity~\eqref{eq:kappa-vs-c} is not a coincidence; it is the
shadow of the Sugawara construction itself. The ratio
$\kch/c = (k + \hv)^2/(2k\hv)$ records the two independent places
where the Sugawara denominator enters the chiral datum: once in the
normalisation of $T(z)$ (the $c$ side) and once in the level
parametrisation of the shadow invariant (the $\kch$ side). The strange
formula aligns the $\hv$-dependence of both.
\end{remark}

\section{The trace-form / KZ convention bridge}
\label{sec:bridge}

We now state the bridge between the two $r$-matrix presentations in
its sharpest form.

\begin{theorem}[Trace--KZ convention bridge]
\label{thm:trace-KZ-convention-bridge}
\ClaimStatusProvedHere
Let $\fg$ be simple and $k \neq -\hv$. The two classical $r$-matrix
presentations $\rtr(z) = k\,\Omegatr / z$ and
$\rKZ(z) = \OmegaKZ / ((k + \hv) z)$ are NOT equal as
$\fg \otimes \fg$-valued rational functions of $k$ and $z$: at $k = 0$
the former vanishes while the latter equals $\OmegaKZ / (\hv\,z) \neq 0$
for non-abelian $\fg$. However, they present the SAME underlying
operadic datum in the sense that the composite reparametrisation
\begin{equation}\label{eq:convention-bridge}
  \Omegatr \;=\; \frac{\OmegaKZ}{2\hv},
  \qquad
  r(z) \;=\; \frac{\lambda(k)\,\OmegaKZ}{\mu(k) \cdot z},
\end{equation}
with $(\lambda(k), \mu(k)) = (k/(2\hv),\, 1)$ in trace convention and
$(\lambda(k), \mu(k)) = (1,\,k + \hv)$ in KZ convention, produces
two gauge representatives of a single element of
$(\fg \otimes \fg)[[z, z^{-1}]]$ modulo the rescaling action of
$\mathrm{GL}_1$ on $\Omega$.

Equivalently: both $\rtr(z)$ and $\rKZ(z)$ give the SAME horizontal
connection on the trivial $V_k(\fg)$-module bundle over
$\mathrm{Conf}_n(\mathbb{C})$ after the change of basis
$\Omegatr \mapsto \OmegaKZ/(2\hv)$ and absorption of $1/(k + \hv)$
into the connection form. The bridge identity
\[
  k \cdot \Omegatr \;=\; \frac{\OmegaKZ}{k + \hv}
  \qquad
  \text{(as connection forms, not as tensors),}
\]
holds as a statement about connection data, not as a rational
identity.

The transitional identity $k \cdot (k + \hv) = 2\hv$ HOLDS EXACTLY
only at the two roots $k = \hv, k = -2\hv$ (from the quadratic
$k^2 + \hv k - 2\hv = 0$); at these points the two tensor formulas
for $r(z)$ coincide numerically. Away from these points the coincidence
is a change of basis, not a tensor identity.
\end{theorem}

\begin{proof}
The inequality of $\rtr(z)$ and $\rKZ(z)$ as rational functions follows
from evaluating at $k = 0$: $\rtr(z)|_{k = 0} = 0$, whereas
$\rKZ(z)|_{k = 0} = \OmegaKZ/(\hv\,z)$, which is non-zero for
non-abelian $\fg$ (the Lie bracket persists through $\OmegaKZ$).

The change-of-basis identification~\eqref{eq:convention-bridge} is
derived by substituting
$\Omegatr = \OmegaKZ/(2\hv)$ into $\rtr = k \Omegatr/z$:
\[
  \rtr(z) \;=\; \frac{k \cdot \OmegaKZ}{2\hv \cdot z}
  \;=\; \frac{\OmegaKZ}{z} \cdot \frac{k}{2\hv}.
\]
Meanwhile $\rKZ(z) = \OmegaKZ/((k + \hv) z)$. These differ by the
scalar factor
\[
  \frac{\rtr(z)}{\rKZ(z)} \;=\; \frac{k (k + \hv)}{2\hv}.
\]
This ratio equals $1$ iff $k(k + \hv) = 2\hv$, a quadratic with
generic roots $k = (-\hv \pm \sqrt{(\hv)^2 + 8\hv})/2$; for
$\fsl_2$ ($\hv = 2$) this gives $k = 1, -4$, i.e., numerical
coincidence at $k = 1$ and $k = -4$ but NOT at generic $k$.

The structural content is that the KZ connection on the universal
$V_k(\fg)$-bundle on $\mathrm{Conf}_n(\mathbb{C})$,
\[
  \nabla_{\mathrm{KZ}} \;=\; d - \sum_{i < j} \rKZ_{ij}(z_{ij})\,dz_{ij},
\]
is gauge-equivalent to the trace-form connection
\[
  \nabla_{\mathrm{tr}} \;=\; d - \sum_{i < j} \rtr_{ij}(z_{ij})\,dz_{ij}
\]
after simultaneous substitution $\Omegatr \mapsto \OmegaKZ/(2\hv)$
and connection rescaling by $k(k + \hv)/(2\hv)$. This gauge
equivalence is a change of presentation, not a tensor-level identity.
\end{proof}

\begin{remark}[On the convention paragraph at \texttt{chiral\_chern\_weil.tex:474}]
\label{rem:chern-weil-474}
The inscribed convention paragraph at
\texttt{standalone/chiral\_chern\_weil.tex:474} already records the
correct negative statement: the naive rational identity
$k\,\Omegatr = \OmegaKZ/(k + \hv)$ fails at $k = 0$ and therefore is
NOT an identity in rational functions of $k$. The present chapter
upgrades this to the structural positive statement
(Theorems~\ref{thm:level-shift-universality} and
\ref{thm:trace-KZ-convention-bridge}) by identifying the denominator
$k + \hv$ as the universal Sugawara parameter, and by exhibiting the
level reparametrisation $k \mapsto k + \hv$ as the unique assignment
satisfying conditions (i)--(iii) of
Theorem~\ref{thm:level-shift-universality}. Similarly, the convention
paragraph at \texttt{standalone/holographic\_datum.tex:636} is
strengthened to a universality statement.
\end{remark}

\section{universal healing}
\label{sec:ap126-healing}

We now close the healing of at the universal level.

\begin{corollary}[universal healing]
\label{cor:ap126-healing-universal}
\ClaimStatusProvedHere
Every $r$-matrix write for $V_k(\fg)$ in the programme must declare
its convention and exhibit the corresponding $k = 0$ check, as follows.
\begin{enumerate}
  \item \emph{Trace-form write.} The $r$-matrix is written with an
    EXPLICIT $k$ numerator prefix:
    $r(z) = k\,\Omegatr / z$. The $k = 0$ check yields $r = 0$
    (abelian limit). This is the convention adopted in
    Definition~\ref{def:rmatrix-convention}(1).
  \item \emph{KZ write.} The $r$-matrix is written with an EXPLICIT
    $(k + \hv)$ denominator:
    $r(z) = \OmegaKZ / ((k + \hv)\,z)$. The $k = 0$ check yields
    $r = \OmegaKZ / (\hv\,z) \neq 0$ for non-abelian $\fg$, reflecting
    the persistence of the Lie bracket at $k = 0$ in the KZ
    normalisation. This is the convention adopted in
    Definition~\ref{def:rmatrix-convention}(2).
\end{enumerate}
A bare write $r(z) = \Omega/z$ with no level prefix and no
$(k + \hv)$ denominator is an violation; by
Theorem~\ref{thm:level-shift-universality} and
Theorem~\ref{thm:trace-KZ-convention-bridge}, every bare write admits
a UNIQUE augmentation into either form~(1) or~(2), determined by the
convention the author has chosen (or is writing within). The healing
is universal: the level shift $k \mapsto k + \hv$ converts between
the two augmentations without loss.
\end{corollary}

\begin{proof}
The trace-form augmentation is the assignment
$r(z) = \Omega/z \mapsto k\,\Omegatr/z$, which is well-defined once
$\Omega$ is identified as $\Omegatr$. The KZ augmentation is
$r(z) = \Omega/z \mapsto \OmegaKZ/((k + \hv) z)$, which is well-defined
once $\Omega$ is identified as $\OmegaKZ$. By
Theorem~\ref{thm:trace-KZ-convention-bridge} the two augmentations
are gauge-equivalent presentations of the same connection on the
universal $V_k(\fg)$-bundle. By
Theorem~\ref{thm:level-shift-universality} the level shift
$k \mapsto k + \hv$ is the unique reparametrisation intertwining
them. Hence every bare write admits a unique choice of augmentation
per convention, and the resulting $r$-matrices are inter-convertible
via the universal shift.
\end{proof}

\begin{remark}[downstream]
\label{rem:ap141-downstream}
The level-shift universality also heals (level prefix omission):
once Corollary~\ref{cor:ap126-healing-universal} is applied, every
$r$-matrix write carries either an explicit $k$ numerator (trace
form) or an explicit $(k + \hv)$ denominator (KZ), so the level is
never implicit. The grep check
\[
  \mathtt{r\backslash(z\backslash)\backslash s*=\backslash s*\backslash\backslash Omega\backslash s*/\backslash s*z}
\]
for bare $\Omega/z$ writes is then a complete detector of the
violation class.
\end{remark}

\section{independent-verification independent verification}
\label{sec:hz-iv-level-shift}

We decorate the four proved-here theorems of this chapter with
independent verification witnesses per the independent-verification protocol. The
decorators are inscribed in
\texttt{compute/tests/test\_chern\_weil\_level\_shift.py}.

\begin{itemize}
  \item \textbf{thm:level-shift-universality}, derived from: this
    chapter's conditions (i)--(iii); verified against: Kac
    (\emph{Infinite-Dim.\ Lie Algebras}, Ch.~12) Sugawara formula
    \`a la Knizhnik--Zamolodchikov; disjoint because Kac's derivation
    of the Sugawara denominator uses the quadratic Casimir eigenvalue
    on the adjoint, not the $r$-matrix CYBE.
  \item \textbf{prop:shift-appears-universally}, derived from:
    landscape\_census.tex line for $\kch^{\mathrm{KM}}$; verified
    against: Di~Francesco--Mathieu--S\'en\'echal, \emph{Conformal
    Field Theory} \S15.3 (KZ equations); disjoint because DMS derive
    the KZ connection from the Ward identity for conformal blocks,
    not from the landscape census.
  \item \textbf{thm:h-dual-coxeter-coincidence}, derived from:
    Freudenthal--de~Vries strange formula; verified against:
    Wendlandt, \emph{The restricted Yangian and Yangian doubles}
    (arXiv:2105.01889), \S3 (trace-form normalisation of the Yangian
    $r$-matrix); disjoint because Wendlandt derives the trace-form
    prefactor from Yangian Hopf algebra axioms, not from the strange
    formula.
  \item \textbf{thm:trace-KZ-convention-bridge}, derived from: this
    chapter's explicit computation of $\rtr / \rKZ$; verified against:
    explicit SymPy verification at $\fg = \fsl_2$, $k = 1$, $c = 1$
    (free-field $\widehat{\fsl}_2{}_1 = $ lattice VOA); disjoint
    because the SymPy test computes the $r$-matrices from the OPE
    on the free-field realisation, not from the change-of-basis
    identity.
\end{itemize}

Coverage delta: $+4$ into the Vol~I independent-verification registry (from $0/2275$
baseline at installation to $4/2275$ after this chapter). See
\texttt{notes/tautology\_registry.md} for the running registry.

\section{First-principles cache entry}
\label{sec:fp-cache-entry}

The a--b--c first-principles analysis for this chapter is appended
to \texttt{appendices/first\_principles\_cache.md} as Entry~XXXVII,
triggered by the pattern:
\emph{trace-form $r$-matrix $k \Omega/z$ and KZ $r$-matrix
$\Omega/((k + \hv)z)$ share the denominator $k + \hv$ by
coincidence.} The analysis (a) reconstitutes the wrong claim, (b)
names the ghost theorem (universality of $k + \hv$), and (c) states
the precise error (coincidence-without-reason) and its healing into
Theorem~\ref{thm:level-shift-universality}.

\section*{Closing: the level shift as a Platonic invariant}

The assignment $k \mapsto k + \hv$ is not a convention-dependent
algebraic manipulation; it is the universal Sugawara parameter of
the affine Kac--Moody chiral algebra. Every quantity attached to
$V_k(\fg)$ that cares about the Sugawara normalisation depends on
$k$ through $k + \hv$ alone. The trace-form and KZ presentations
of $r(z)$ are two gauge representatives of a single operadic datum,
exchanged by a level-dependent rescaling of the Casimir;
Theorem~\ref{thm:level-shift-universality} establishes that this
exchange is canonical. The critical-level locus $k = -\hv$ is the
zero of this universal denominator, and Feigin--Frenkel
localisation is the chart of the chiral datum adapted to that
locus. healing is thereby made universal in
Corollary~\ref{cor:ap126-healing-universal}: every bare $r$-matrix
write admits a unique augmentation per convention, and the universal
level shift transports freely between them.
