\chapter{Chiral Hochschild cohomology and Koszul duality}
\label{chap:deformation-theory}

\index{deformation theory!chiral|textbf}
\index{Hochschild cohomology!chiral|textbf}
\index{three Hochschild theories!discipline}

\begin{remark}[Three Hochschild theories: discipline]
\label{rem:three-hochschild-discipline}

The symbol \emph{Hochschild} carries three meanings in the
programme; the present chapter is concerned with exactly one. The
chiral Hochschild complex $\ChirHoch^*(\cA)$ defined here is the
tangent complex of the chiral MC moduli on a curve, an
$E_\infty$-chiral input producing an output concentrated in
degrees~$\{0,1,2\}$ (Theorem~H below). It is distinct from
\textup{(a)} the topological Hochschild $\mathrm{HH}^*_{\mathrm{top}}$
of an $E_1$-algebra in spectra, whose output is the $E_2$-Gerstenhaber
algebra of Deligne; and from \textup{(b)} the categorical Hochschild
$\mathrm{HH}^*_{\mathrm{cat}}$ of a dg category, whose output is an
$E_2$-algebra carrying CY shifted Poisson structure. The geometry
determines which Hochschild: a curve $X$ produces ChirHoch, a
formal disk over a point produces HH$_{\mathrm{top}}$, a CY dg
category produces HH$_{\mathrm{cat}}$. Throughout this chapter
``Hochschild'' means $\ChirHoch^*$; the other two are signposted
explicitly when invoked.
\end{remark}

The MC element $\Theta_\cA \in \MC(\gAmod)$ controls all of chiral
Koszul duality, but how rigid is the moduli it lives in? Without
knowing the tangent complex to
$\MC(\gAmod)/\mathrm{gauge}$, every deformation, obstruction, and
bulk-field coupling remains inaccessible. The chiral Hochschild
complex $\ChirHoch^*(\cA)$ is that tangent complex;
Theorem~H proves it is concentrated in degrees $\{0,1,2\}$ on the
Koszul locus, so the MC moduli has cohomological
amplitude~$[0,2]$, and the Koszul duality
$\ChirHoch^n(\cA) \cong \ChirHoch^{2-n}(\cA^!)^\vee \otimes \omega_X$
is Verdier duality on this tangent space. The amplitude is the
output of the Koszul Reflection
$K^{2}\simeq\mathrm{id}$
(Theorem~\ref{thm:koszul-reflection}) read on the chiral derived
centre $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA) = \ChirHoch^*(\cA,\cA)$:
the curve dimension $\dim_\mathbb{C} X = 1$ contributes the curve
amplitude $[0,1]$, the bigraded Verdier shift contributes the extra
$[1]$, and Koszul collapse forces the diagonal to be the only
contributing direction. The structural source of the
$\{0,1,2\}$ concentration is therefore $E_3$-rigidity at a point
applied to $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$, with PBW collapse
underwriting the chain-level statement.

The cyclic deformation complex $\Defcyc(\cA)$
(Definition~\ref{def:cyclic-deformation-elementary}) is the cyclic
refinement of $\ChirHoch^*(\cA)$.
The complementarity
theorem (Theorem~\ref{thm:quantum-complementarity-main}) identifies
the $\cA$-visible and $\cA^!$-visible tangent directions as
complementary Lagrangians in the shifted-symplectic MC moduli.

chiral Hochschild complexes
carry natural brace and $E_2$ structures. The convolution dg~Lie
algebra $\Convstr(\barB(\cA), \cA)$ governing deformations is the
strict model of the $L_\infty$ deformation object
$\Convinf(\barB(\cA), \cA)$
(Theorem~\ref{thm:operadic-homotopy-convolution}).
The modular cyclic deformation complex
$\Defcyc^{\mathrm{mod}}(\cA)$
(Definition~\ref{def:modular-cyclic-deformation-complex}),
strict model of $\Definfmod(\cA)$
(Remark~\ref{rem:modular-cyc-strictification}),
extends these structures to the full modular regime.

Two algebraic objects govern the open/closed dictionary:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Bar/cobar} classifies \emph{twisting morphisms}:
 universal couplings between $\cA$ and its Koszul dual $\cA^!$
 (Chapter~\ref{chap:bar-cobar}). These are the operadic data
 encoding how the closed sector twists the open sector.
\item \emph{Chiral Hochschild cochains}
 $C^\bullet_{\mathrm{ch}}(\cA, \cA)$ classify \emph{bulk operators}
 acting on the boundary
 (Theorem~\ref{thm:chiral-deligne-tamarkin}). The brace dg algebra
 structure makes $C^\bullet_{\mathrm{ch}}$ the universal bulk:
 it is the terminal local chiral Swiss-cheese pair over $\cA$, and
 its cohomology $Z_{\mathrm{ch}}(\cA) = H^*(C^\bullet_{\mathrm{ch}},
 \delta)$ is the chiral derived center
 (Definition~\ref{def:thqg-chiral-derived-center}).
\end{enumerate}
The open/closed MC element $\Theta^{\mathrm{oc}}_\cA$
(\S\ref{sec:thqg-open-closed-realization}) packages both:
its closed projection is the bar-intrinsic $\Theta_\cA$
(Theorem~\ref{thm:mc2-bar-intrinsic}), and its mixed projection
is the bulk-to-boundary coupling through
$C^\bullet_{\mathrm{ch}}(\cA, \cA)$. The shadow obstruction tower
$(\kappa, \mathfrak{C}, \mathfrak{Q}, \ldots)$ lives in the closed
sector; the annulus trace
$\int_{S^1} \mathcal{M} \simeq HH_*(\mathcal{M})$
(Theorem~\ref{thm:thqg-annulus-trace}) is the first modular shadow
of the open sector.

\section{Deformations of a chiral algebra}

Let $\mathcal{A}$ be a chiral algebra on a smooth projective curve~$X$,
with chiral product
$\mu\colon j_*j^*(\mathcal{A}\boxtimes\mathcal{A})\to\Delta_*\mathcal{A}$
(Chapter~\ref{ch:algebraic-foundations}).
\index{obstruction theory|textbf}
A \emph{first-order deformation} of~$\mathcal{A}$ is a
$\mathcal{D}_X$-module
$\mathcal{A}_\epsilon = \mathcal{A}\oplus\epsilon\,\mathcal{A}$
over $k[\epsilon]/(\epsilon^2)$, equipped with a chiral product
$\mu_\epsilon = \mu + \epsilon\,\phi$, where
$\phi\colon j_*j^*(\mathcal{A}\boxtimes\mathcal{A})\to\Delta_*\mathcal{A}$
is a $\mathcal{D}_X$-bimodule map.

The deformed product $\mu_\epsilon$ must satisfy the Borcherds
identity~\cite{Bor92,BD04}:
for sections $a,b,c$ of~$\mathcal{A}$ at pairwise distinct points
$z_1,z_2,z_3\in X$,
\[
\begin{aligned}
 &\operatorname{Res}_{z_1\!=z_2}\!\mu_\epsilon(a(z_1),\mu_\epsilon(b(z_2),c(z_3)))
 - \operatorname{Res}_{z_1\!=z_2}\!\mu_\epsilon(b(z_2),\mu_\epsilon(a(z_1),c(z_3)))\\
 &\qquad= \operatorname{Res}_{z_2\!=z_3}\!\mu_\epsilon(\mu_\epsilon(a(z_1),b(z_2)),c(z_3)).
\end{aligned}
\]
Expanding modulo~$\epsilon^2$ and using the Borcherds identity for~$\mu$,
the $\epsilon$-coefficient gives:
\begin{equation}\label{eq:deformation-cocycle}
\begin{split}
 \operatorname{Res}_{z_1\!=z_2}\!\bigl[\phi(a,\mu(b,c))
 &+ \mu(a,\phi(b,c))\\
 &- \phi(b,\mu(a,c))
 - \mu(b,\phi(a,c))\bigr]\\
 &= \operatorname{Res}_{z_2\!=z_3}\!\bigl[\phi(\mu(a,b),c)
 + \mu(\phi(a,b),c)\bigr].
\end{split}
\end{equation}
This is a cocycle condition: $\phi$ is closed in a complex whose
differential is built from~$\mu$ via the residue operations above.
That complex is the \emph{chiral Hochschild complex}
$C^{\bullet}_{\mathrm{chiral}}(\mathcal{A})$, constructed in
\S\ref{subsec:hochschild-duality}.

The cocycle condition~\eqref{eq:deformation-cocycle} involves three
marked points on~$X$ and residues as pairs collide. An $n$-cochain
in the chiral Hochschild complex involves $(n+2)$ points on~$X$;
the differential acts by residues along the collision divisors
$D_{ij}=\{z_i=z_j\}$ in~$X^{n+2}$. The complex lives on the
configuration space
$C_{n+2}(X)=\{(z_1,\ldots,z_{n+2})\in X^{n+2}: z_i\neq z_j\}$,
and the differential extends to the Fulton--MacPherson
compactification $\overline{C}_{n+2}(X)$ as the bar
differential does (Chapter~\ref{chap:bar-cobar}).

At genus $g\geq 1$, the fiberwise differential satisfies
$\dfib^{\,2}=\kappa(\cA)\cdot\omega_g$
(Chapter~\ref{ch:heisenberg-frame};
Convention~\ref{conv:higher-genus-differentials}), so the bar complex
is a curved $A_\infty$-algebra. The curvature scalar~$\kappa(\cA)$
obstructs lifting a genus-$0$ deformation to genus~$g$.
Complementarity
(Theorem~\ref{thm:quantum-complementarity-main}) identifies
$Q_g(\cA)$ and $Q_g(\cA^!)$ as complementary Lagrangians in a
shifted-symplectic space built from
$H^*(\overline{\mathcal{M}}_g,\mathcal{Z}(\cA))$. At the
chiral Hochschild level, Koszul duality exchanges deformations and
obstructions:
$\ChirHoch^n(\cA)\cong \ChirHoch^{2-n}(\cA^!)^\vee\otimes\omega_X$
(Remark~\ref{rem:nc-hodge-degeneration}).

\section{Construction of the chiral Hochschild complex}

\subsection{The cochain spaces}

A degree-$n$ cochain involves $(n+2)$ marked points on~$X$: one output, $n$ inputs, and one evaluation point.

\begin{definition}[Chiral Hochschild complex, geometric realization]
\label{def:chiral-hochschild-complex}
\index{Hochschild complex!chiral!geometric realization|textbf}
For a chiral algebra $\mathcal{A}$ on a smooth curve $X$, define the degree $n$ cochains as
\[
C^n_{\text{chiral}}(\mathcal{A}) = \Gamma\left(\overline{C}_{n+2}(X), j_*j^*\mathcal{A}^{\boxtimes (n+2)} \otimes \Omega^n_{\overline{C}_{n+2}(X)}(\log D)\right)
\]
where:
\begin{itemize}
\item $\overline{C}_{n+2}(X)$ is the Fulton--MacPherson compactification
\item $j: C_{n+2}(X) \to \overline{C}_{n+2}(X)$ is the open embedding
\item $\mathcal{A}^{\boxtimes (n+2)}$ denotes the external tensor product on $X^{n+2}$
\item $\Omega^n_{\overline{C}_{n+2}(X)}(\log D)$ are $n$-forms with logarithmic poles along the boundary divisor $D$
\end{itemize}
This is the \emph{geometric Fulton--MacPherson model} of the chiral
Hochschild complex; the algebraic Ext model
$\Ext^*_{\cA^e}(\cA,\cA)$
\textup{(}Definition~\textup{\ref{def:chirHoch-Ext}} in
Chapter~\textup{\ref{chap:koszul-pair-structure}}\textup{)} computes
the same chiral derived endomorphism centre under
Theorem~\textup{\ref{thm:geometric-chiral-hochschild}}; the bigraded
Verdier model is recorded in
Definition~\textup{\ref{def:bigraded-hochschild}} of
Chapter~\textup{\ref{chap:higher-genus}}. All three
models compute $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ and have
universal cohomological amplitude~$[0,2]$ on $\Kosz(X)$
(Theorem~H, Theorem~\textup{\ref{thm:main-koszul-hoch}}); the
amplitude is the trace shadow of $K^{2}\simeq\mathrm{id}$
(Theorem~\textup{\ref{thm:koszul-reflection}}).
\end{definition}

Explicitly, a degree $n$ cochain is a sum of expressions
\[
\phi = \sum_I a_0^{(I)}(z_0) \otimes a_1^{(I)}(z_1) \otimes \cdots \otimes a_n^{(I)}(z_n) \otimes a_{\infty}^{(I)}(z_{\infty}) \otimes \omega_I
\]
where $a_i^{(I)} \in \mathcal{A}$ and $\omega_I$ is an $n$-form on $\overline{C}_{n+2}(X)$ with logarithmic singularities.

\subsection{The differential: three components}

The chiral Hochschild differential
$d_{\mathrm{Hoch}}: C^n_{\text{chiral}} \to C^{n+1}_{\text{chiral}}$
has three components reflecting the algebraic, geometric, and operadic
structures:

\begin{theorem}[The chiral Hochschild differential; \ClaimStatusProvedHere]
\label{thm:chiral-hochschild-differential}
The differential decomposes as
\[
d_{\mathrm{Hoch}} = d_{\text{int}} + d_{\text{fact}} + d_{\text{config}}
\]
where:
\begin{enumerate}
\item $d_{\text{int}}$: internal differential from the $\mathcal{D}_X$-module structure
\item $d_{\text{fact}}$: factorization using chiral multiplication 
\item $d_{\text{config}}$: de Rham differential on configuration space
\end{enumerate}
\end{theorem}

\begin{proof}
We expand $d_{\mathrm{Hoch}}^{\,2}
= (d_{\text{int}} + d_{\text{fact}}
+ d_{\text{config}})^2$ into six terms (three squares and
three anticommutators) and verify that each vanishes on a
generic cochain $\phi \in C^n_{\text{chiral}}$.

\emph{(I) Pure squares.}

\emph{(I.1)} $d_{\text{int}}^2(\phi) = 0$.
The internal differential $d_{\text{int}}$ acts on each
tensor factor $a_i$ by the $\mathcal{D}_X$-module differential
$d_\mathcal{A}$, alternating signs. Since $d_\mathcal{A}^2 = 0$
and the signs follow the standard Koszul rule, this is the
usual chain complex identity.

\emph{(I.2)} $d_{\text{config}}^2(\phi) = 0$.
$d_{\text{config}} = d_{\overline{C}_{n+2}(X)}$ is the
de~Rham differential on the compactified configuration space.
Since $d_{\mathrm{dR}}^2 = 0$, this is immediate.

\emph{(I.3)} $d_{\text{fact}}^2(\phi) = 0$.
Applied to $\phi \in C^n$, $d_{\text{fact}}^2$ composes two
chiral multiplications at distinct pairs of colliding points.
For each pair of collisions $(z_i = z_j)$ and $(z_k = z_l)$
with $\{i,j\} \cap \{k,l\} = \varnothing$, the two residue
extractions commute. For overlapping pairs (sharing a point),
the double residue
$\mathrm{Res}_{z_i = z_j}\mathrm{Res}_{z_j = z_k}$ is the
iterated OPE, which cancels with
$\mathrm{Res}_{z_j = z_k}\mathrm{Res}_{z_i = z_j}$ by
associativity of the chiral product: $\mu \circ (\mu \otimes
\mathrm{id}) = \mu \circ (\mathrm{id} \otimes \mu)$ on the
localizations $j_*j^*$ (the Borcherds identity).

\emph{(II) Mixed anticommutators.}

\emph{(II.1)} $\{d_{\text{int}}, d_{\text{fact}}\}(\phi) = 0$.
The chiral product $\mu\colon j_*j^*(\mathcal{A} \boxtimes
\mathcal{A}) \to \Delta_*\mathcal{A}$ is a morphism of
$\mathcal{D}_X$-modules, so $d_\mathcal{A} \circ \mu =
\mu \circ (d_\mathcal{A} \boxtimes \mathrm{id} +
\mathrm{id} \boxtimes d_\mathcal{A})$. Expanding the
anticommutator term by term, each
$d_\mathcal{A}(\mu(a_i, a_j))$ equals
$\mu(d_\mathcal{A} a_i, a_j) + (-1)^{|a_i|}
\mu(a_i, d_\mathcal{A} a_j)$,
and the signs from $d_{\text{int}}$ and $d_{\text{fact}}$
cancel pairwise.

\emph{(II.2)} $\{d_{\text{int}}, d_{\text{config}}\}(\phi) = 0$.
The logarithmic forms
$\omega \in \Omega^*_{\overline{C}_{n+2}}(\log D)$
are \emph{universal}: they depend only on the configuration
space coordinates $z_i$, not on the algebra data $a_i$.
Therefore $d_\mathcal{A}$ acts only on the $a_i$ factors,
while $d_{\mathrm{dR}}$ acts only on $\omega$. Since the
two differentials act on different tensor factors:
$d_\mathcal{A}(a_i \otimes \omega) =
(d_\mathcal{A} a_i) \otimes \omega$ and
$d_{\mathrm{dR}}(a_i \otimes \omega) =
a_i \otimes d_{\mathrm{dR}}\omega$,
the anticommutator reduces to
$(d_\mathcal{A} \otimes d_{\mathrm{dR}} +
d_{\mathrm{dR}} \otimes d_\mathcal{A})(a_i \otimes \omega)
= 0$ by the Koszul sign rule for the tensor product of
chain complexes.

\emph{(II.3)} $\{d_{\text{fact}}, d_{\text{config}}\}(\phi) = 0$.
The cancellation requires the
Arnold--Orlik--Solomon relations.

On a degree-$1$ cochain
$\phi = a_1 \otimes a_2 \otimes a_3 \otimes
\eta_{12} \in C^1$ (the smallest nontrivial case,
with three points $z_1, z_2, z_3$), the two compositions act
as:
\begin{align*}
(d_{\text{config}} \circ d_{\text{fact}})(\phi)
&= d_{\mathrm{dR}}\Bigl(
 \mathrm{Res}_{z_1 = z_2}\bigl[a_1 a_2 \otimes a_3
 \otimes \eta_{12}\bigr] \Bigr), \\
(d_{\text{fact}} \circ d_{\text{config}})(\phi)
&= \sum_{i<j}
 \mathrm{Res}_{z_i = z_j}\bigl[a_1 \otimes a_2 \otimes a_3
 \otimes d_{\mathrm{dR}}\eta_{12}\bigr].
\end{align*}

The key identity is Arnold's relation
\cite{Arnold69}: for the logarithmic 1-forms
$\eta_{ij} = d\log(z_i - z_j)$ on $C_3(X)$,
\begin{equation}\label{eq:arnold-three-point}
\eta_{12} \wedge \eta_{23}
+ \eta_{23} \wedge \eta_{31}
+ \eta_{31} \wedge \eta_{12} = 0.
\end{equation}
Equivalently, $d_{\mathrm{dR}}\eta_{12}$ (which is
supported on the boundary divisor) decomposes as a sum of
residues at $D_{13}$ and $D_{23}$:
\[
d_{\mathrm{dR}}(\eta_{12})
\;\equiv\;
-\eta_{23}\big|_{D_{12}} - \eta_{31}\big|_{D_{12}}
\pmod{\text{smooth forms}}.
\]
In each residue term, $d_{\text{fact}}$ extracts the OPE
at a collision, and $d_{\text{config}}$ produces the
boundary form. The Arnold relation
\eqref{eq:arnold-three-point} ensures these contributions
cancel pairwise, yielding
$\{d_{\text{fact}}, d_{\text{config}}\}(\phi) = 0$.

For general $n$, the argument extends by applying the
generalized Arnold relations on $\overline{C}_{n+2}(X)$
(Theorem~\ref{thm:arnold-relations}): every boundary
stratum of $\overline{C}_{n+2}$ where two points collide
contributes a residue (from $d_{\text{fact}}$) and a
boundary form (from $d_{\text{config}}$), and the
Arnold relations ensure these pair up with opposite signs.
\end{proof}

\subsection{Explicit formula for the differential}

For a cochain $\phi \in C^n_{\text{chiral}}$, the differential acts by:

\begin{align}
(d_{\text{int}}\phi)(&z_0,\ldots,z_{n+1}) = \sum_{i=0}^{n+1} (-1)^i d_{\mathcal{A}}(\phi(z_0,\ldots,\hat{z}_i,\ldots,z_{n+1})) \\
(d_{\text{fact}}\phi)(&z_0,\ldots,z_{n+1}) = \sum_{i=1}^n (-1)^i \text{Res}_{z_i = z_0} \phi(\mu(z_0,z_i),z_1,\ldots,\hat{z}_i,\ldots,z_{n+1}) \\
&+ \sum_{1 \leq i < j \leq n} (-1)^{i+j} \phi(z_0,\ldots,\mu(z_i,z_j),\ldots,\hat{z}_i,\ldots,\hat{z}_j,\ldots,z_{n+1}) \\
(d_{\text{config}}\phi)(&z_0,\ldots,z_{n+1}) = d_{\overline{C}_{n+2}}(\phi)
\end{align}

where $\hat{z}_i$ denotes omission and $\mu$ is the chiral multiplication.

\section{Computing cohomology via bar-cobar resolution}

\subsection{The resolution strategy}

\begin{theorem}[chiral Hochschild via bar-cobar; \ClaimStatusProvedHere]\label{thm:hochschild-bar-cobar}
\textup{[Regime: quadratic on the Koszul locus
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

For any chiral Koszul algebra $\mathcal{A}$
\textup{(}Definition~\textup{\ref{def:chiral-koszul-pair})},
there is a quasi-isomorphism
\[
C^{\bullet}_{\text{chiral}}(\mathcal{A}) \simeq \text{Hom}_{\text{ChirAlg}}(\Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A})), \mathcal{A})
\]
where $\Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A}))$ is the cobar construction of the bar complex.
\end{theorem}

\begin{proof}
The proof has three steps:

\emph{Step 1: Bar gives cofree resolution.} 
The geometric bar complex $\overline{B}^{\text{ch}}(\mathcal{A})$ constructed in Chapter~\ref{chap:bar-cobar} is a cofree chiral coalgebra resolving $\mathcal{A}$:
\[
\overline{B}^{\text{ch}}(\mathcal{A}) \xrightarrow{\epsilon} \mathcal{A}
\]

\emph{Step 2: Cobar gives free resolution.}
Applying the cobar functor (Chapter~\ref{chap:bar-cobar}) yields a free chiral algebra resolution:
\[
\Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A})) \xrightarrow{\eta} \mathcal{A}
\]

\emph{Step 3: Hom computes Ext.}
By definition, 
\[
\text{Ext}^n_{\text{ChirAlg}}(\mathcal{A}, \mathcal{A}) = H^n(\text{Hom}_{\text{ChirAlg}}(\Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A})), \mathcal{A}))
\]
The left side is precisely $\ChirHoch^n(\mathcal{A})$ by definition.
\end{proof}

\subsection{The spectral sequence}

\begin{theorem}[chiral Hochschild spectral sequence; \ClaimStatusProvedHere]\label{thm:hochschild-spectral-sequence}
There exists a spectral sequence
\[
E_1^{n,q} = H^q(\overline{C}_{n+2}(X), \mathcal{A}^{\boxtimes (n+2)} \otimes \Omega^n_{\log}) \Rightarrow \ChirHoch^{n+q}(\mathcal{A})
\]
where $n$ is the bar degree (number of internal insertions) and $q$ is the sheaf cohomology degree, which are independent indices.
\end{theorem}

\begin{proof}
The chiral Hochschild complex $\ChirHoch^*(\mathcal{A})$ is a double complex with horizontal differential $d_{\mathrm{bar}}$ (the bar differential of Definition~\ref{def:bar-differential-complete}) and vertical differential $d_{\mathrm{sheaf}}$ (sheaf cohomology on configuration spaces). Filter by bar degree: $F^n = \bigoplus_{m \geq n} \ChirHoch^{m,*}$. The resulting spectral sequence has $E_0^{n,q} = \Gamma(\overline{C}_{n+2}(X), \mathcal{A}^{\boxtimes(n+2)} \otimes \Omega^n_{\log})$ with $d_0 = d_{\mathrm{sheaf}}$, so $E_1^{n,q} = H^q(\overline{C}_{n+2}(X), \mathcal{A}^{\boxtimes(n+2)} \otimes \Omega^n_{\log})$. Convergence follows from the bounded-below hypothesis on $\mathcal{A}$ and the finite cohomological dimension of configuration spaces.
\end{proof}

For the cyclic refinement relating chiral Hochschild to cyclic homology via Connes' operator, see Theorem~\ref{thm:HC-spectral-sequence}. For formal chiral algebras (quasi-isomorphic to their cohomology), the spectral sequence above degenerates at $E_1$, giving:
\[
\ChirHoch^k(\mathcal{A}) \cong \bigoplus_{n+q=k} H^q(\overline{C}_{n+2}(X), \mathcal{A}^{\boxtimes (n+2)} \otimes \Omega^n_{\log})
\]

\section{Koszul duality for chiral algebras}

\subsection{Quadratic chiral algebras and their duals}

\begin{definition}[Quadratic chiral algebra]
A chiral algebra $\mathcal{A}$ is \emph{quadratic} if it admits a presentation
\[
\mathcal{A} = T_{\text{chiral}}(\mathcal{V})/(R)
\]
where:
\begin{itemize}
\item $\mathcal{V}$ is a locally free $\mathcal{O}_X$-module of generators
\item $T_{\text{chiral}}(\mathcal{V})$ is the free chiral algebra on $\mathcal{V}$
\item $R \subset j_*j^*(\mathcal{V} \boxtimes \mathcal{V})$ consists of quadratic relations
\end{itemize}
\end{definition}

The free chiral algebra requires care. Following Beilinson--Drinfeld:

\begin{definition}[Free chiral algebra]
The free chiral algebra on $\mathcal{V}$ is
\[
T_{\text{chiral}}(\mathcal{V}) = \bigoplus_{n \geq 0} \pi_{n*}\left(j_*j^*\mathcal{V}^{\boxtimes n} \otimes \mathcal{D}_{C_n(X)/X}\right)^{\Sigma_n}
\]
where $\pi_n: C_n(X) \to X$ is the projection and $\mathcal{D}_{C_n(X)/X}$ denotes relative differential operators.
\end{definition}

\begin{definition}[Koszul dual]
The Koszul dual of a quadratic chiral algebra $\mathcal{A}$ is
\[
\mathcal{A}^! = T_{\text{chiral}}(\mathcal{V}^*)/(R^{\perp})
\]
where:
\begin{itemize}
\item $\mathcal{V}^* = \mathcal{H}om_{\mathcal{O}_X}(\mathcal{V}, \omega_X)$ is the dual shifted by the canonical bundle
\item $R^{\perp}$ consists of relations orthogonal to $R$ under the canonical pairing
\[
\langle \cdot, \cdot \rangle: j_*j^*(\mathcal{V}^* \boxtimes \mathcal{V}) \to j_*\omega_{X^2 \setminus \Delta}
\]
\end{itemize}
\end{definition}

\begin{remark}[Three objects]\label{rem:koszul-dual-meaning}
The bar construction $\bar{B}^{\mathrm{ch}}(\cA)$ is the
bar \emph{coalgebra}: a conilpotent dg coalgebra cogenerated
by~$\mathcal{V}^*$ with corelations~$R^{\perp}$.
Its bar cohomology
\[
\cA^i := H^*\bigl(\bar{B}^{\mathrm{ch}}(\cA)\bigr)
\]
is the dual \emph{coalgebra}. The Koszul dual \emph{algebra}
is obtained only after Verdier duality on the curve:
\[
\cA^! := \mathbb{D}_X(\cA^i).
\]
Only on finite-type lanes does this reduce to an ordinary
graded linear dual. The cobar of the bar recovers~$\cA$
itself:
$\Omega(\bar{B}^{\mathrm{ch}}(\cA)) \simeq \cA$
\textup{(}Theorem~\ref{thm:bar-cobar-inversion-qi}\textup{)}.
Thus the corrected comparison chain is
\[
\bar{B}^{\mathrm{ch}}(\cA)
\;\longrightarrow\;
\cA^i
\;\xrightarrow{\ \mathbb{D}_X\ }\;
\cA^!,
\]
with inversion $\Omega(\bar{B}^{\mathrm{ch}}(\cA)) \simeq \cA$
separate from Koszul duality.
\end{remark}

\begin{example}[Explicit correspondence for Heisenberg]
For the Heisenberg chiral algebra $\mathcal{H}_k$ at level~$k$ with generator $\alpha(z)$ and OPE:
\[\alpha(z)\alpha(w) \sim \frac{k}{(z-w)^2}\]

The Koszul dual $\mathcal{H}^!$ has:
\begin{itemize}
\item \emph{Dual generator}: $\alpha^*(z)$ with $\langle \alpha, \alpha^* \rangle = 1$ under residue pairing
\item \emph{Coproduct}: 
 \[\Delta(\alpha^*) = \alpha^* \otimes 1 + 1 \otimes \alpha^* + \text{(higher order terms)}\]
 encoding the dual of the commutative algebra structure
\item \emph{Bar construction}: $\bar{B}^{\text{ch}}(\mathcal{H})$ consists of forms like:
 \[\alpha(z_1) \otimes \cdots \otimes \alpha(z_n) \otimes \eta_{12} \wedge \eta_{23} \wedge \cdots\]
 whose residues extract the coproduct coefficients
\end{itemize}

The cobar of the bar recovers $\mathcal{H}$ itself: $\Omega^{\text{ch}}(\bar{B}^{\text{ch}}(\mathcal{H})) \simeq \mathcal{H}$ (Theorem~\ref{thm:bar-cobar-inversion-qi}).
\end{example}

\begin{remark}[Koszul dual versus dual]
``Koszul dual'' emphasizes the derived character
(bar-cobar construction, quasi-isomorphisms, involutivity:
$(\mathcal{A}^!)^! \simeq \mathcal{A}$). For quadratic $\mathcal{A}$,
this recovers the classical quadratic dual.
\end{remark}

\subsection{The universal twisting morphism}

The universal twisting morphism
$\pi\colon \barB_X(\cA) \to \cA$
(Proposition~\ref{prop:universal-twisting-adjunction}) controls
all bar-cobar identifications in this chapter. Twisting morphisms
are MC elements in the convolution algebra $\mathrm{Hom}(C, A)$
(Definition~\ref{def:twisting-morphism}). The natural bijection
$\mathrm{Tw}(C, A) \cong \mathrm{Hom}(C, B(A)) \cong
\mathrm{Hom}(\Omega(C), A)$
mediates the bar-cobar adjunction
(Proposition~\ref{prop:universal-twisting-adjunction}(iii)); for the
geometric realization as a propagator integral, see
Remark~\ref{rem:twisting-as-propagator}.

\begin{example}[Twisting for fermion-boson duality]
\label{ex:fermion-boson-twisting}
For the Koszul pair (free fermions $\mathcal{F}$, $\beta\gamma$
system), the universal twisting morphism
$\pi\colon \barB^{\mathrm{ch}}(\mathcal{F}) \to \mathcal{F}$
takes the explicit form
$\pi(\psi^*)(z) = \operatorname{Res}_{w=z}\, \psi(w) \cdot \frac{dw}{z-w}$,
implementing the fermion-boson correspondence at the MC level
(Remark~\ref{rem:twisting-as-propagator}).
\end{example}

\subsection{Main duality theorem}\label{subsec:hochschild-duality}

\begin{lemma}[Fulton--MacPherson collapse and chiral Hochschild duality
shift; \ClaimStatusProvedHere]
\label{lem:hochschild-shift-computation}
\index{Hochschild cohomology!duality shift computation}
For a chiral Koszul pair $(\cA, \cA^!)$ on a smooth projective
curve~$X$, and for each bar degree~$p$, let
$F_p^\bullet \overline{C}_{p+2}(X)$ denote the
Fulton--MacPherson collision-depth filtration by closed unions of
strata of codimension at least the filtration index.
The induced filtration on the bigraded chiral Hochschild complex
\textup{(}Definition~\textup{\ref{def:bigraded-hochschild})}
gives a first-quadrant spectral sequence
\begin{equation}\label{eq:hoch-fm-filtration}
E_1^{r,s}(p)
\;=\;
H^{r+s}\!\Bigl(
\operatorname{gr}_{F_p}^{\,r}
CH^{p,\bullet}_{\mathrm{ch}}(\cA)
\Bigr)
\;\Longrightarrow\;
H^{r+s}\!\bigl(CH^{p,\bullet}_{\mathrm{ch}}(\cA)\bigr).
\end{equation}
On the Koszul locus this spectral sequence has:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Curve-level $E_2$ page:}
 \begin{equation}\label{eq:hoch-fm-e2}
 E_2^{r,s}(p)=0 \text{ for } s\neq p,
 \qquad
 E_2^{r,p}(p)\cong
 \Ext_{\mathcal{D}_X}^r\!\bigl((\cA^!)_p,\omega_X\bigr).
 \end{equation}
\item \emph{$E_2$-degeneration:} all higher differentials
 $d_m$ with $m\geq 2$ vanish. Equivalently,
 $E_2(p)=E_\infty(p)$.
\item \emph{Uniform shift:} the geometric Verdier shift
 $[p+2]$ from $\overline{C}_{p+2}(X)$ and the totalization shift
 $[-p]$ from
 $RHH_{\mathrm{ch}}(\cA) :=
 \operatorname{Tot}(\bigoplus_{p \geq 0}
 CH^{p,\bullet}_{\mathrm{ch}}(\cA)[-p])$
 combine to the constant shift~$[2]$.
\item \emph{Amplitude bound:} because $\dim_{\mathbb{C}} X = 1$,
 \[
 \Ext_{\mathcal{D}_X}^r\!\bigl((\cA^!)_p,\omega_X\bigr)=0
 \qquad\text{for } r\notin\{0,1,2\}.
 \]
\end{enumerate}
\end{lemma}

\begin{proof}
Fix~$p$.
The FM compactification $\overline{C}_{p+2}(X)$ is stratified by
collision forests; the closed filtration by collision codimension
induces~\eqref{eq:hoch-fm-filtration}.
Each graded piece is a finite direct sum of external tensor products
of a coherent $\mathcal{D}_X$-module on the base curve with the
logarithmic de~Rham complex of a product of local model fibers
$\FM_m(\mathbb{C})$.
The local complex on the fiber is exactly the bar complex governing
iterated OPE residues at the corresponding collision pattern.

By Theorem~\ref{thm:bar-concentration}, the local bar cohomology is
concentrated in bar-differential degree~$0$.
Writing
\[
\cA^i_p := H^{p,0}\!\bigl(\bar{B}^{\mathrm{ch}}(\cA)\bigr),
\]
the associated graded of the collision-depth filtration is therefore
quasi-isomorphic to a complex on the base curve with coefficient
object~$\cA^i_p$.
Applying degreewise Verdier duality on~$X$ gives the
degree-$p$ piece of the Koszul dual algebra,
\[
(\cA^!)_p = \mathbb{D}_X(\cA^i_p),
\]
which yields the $E_2$-page description~\eqref{eq:hoch-fm-e2}.

The higher differentials vanish for either of two standard reasons.
First, the local fibers $\FM_m(\mathbb{C})$ are formal for
$m\geq 2$ by the configuration-space formality package
\textup{(}Proposition~\textup{\ref{prop:en-formality}}\textup{)},
so after passing to fiber cohomology there is no remaining
chain-level room for $d_m$ with $m\geq 2$.
Equivalent phrasing: the same strata carry pure mixed Hodge
structures, and Deligne strictness forbids a nonzero
weight-changing differential beyond~$E_2$.
Thus $E_2(p)=E_\infty(p)$.

For the shift, Serre--Verdier duality on the smooth proper variety
$\overline{C}_{p+2}(X)$ contributes $[p+2]$, since
$\dim_{\mathbb{C}}\overline{C}_{p+2}(X)=p+2$.
The totalization of the bigraded chiral Hochschild complex contributes
$[-p]$, so the net shift on every surviving $E_\infty$-term is
$(p+2)-p=2$.
The remaining twist is the base-curve dualizing sheaf~$\omega_X$.

Finally, on a smooth complex curve the global Ext functor for
holonomic $\mathcal{D}_X$-modules has amplitude~$[0,2]$.
Hence the only nonzero columns on the $E_2$-page are
$r=0,1,2$, proving the amplitude statement.
\end{proof}

\begin{lemma}[Quadratic-chiral Koszul transfer; \ClaimStatusProvedHere]
\label{lem:chiral-quadratic-koszul}
\index{Koszul duality!quadratic chiral transfer|textbf}
\index{Fresse!quadratic operadic Koszul}
Let $\cP$ be a quadratic chiral operad on the smooth curve~$X$
with generators in degree~$2$ and relations in degree~$3$, and
let $\cP^{!}$ denote its chiral operadic Koszul dual
\textup{(}constructed by $\cD_X$-linear duality on the space
of relations, with the chiral pairing induced by OPE residue
at the principal collision\textup{)}.  Then there is a
degree-preserving chain map
\[
\sigma \;\colon\; \cP^{!}
\;\longrightarrow\;
T^{c}\!\bigl(s^{-1}\,\overline{\cP}\bigr)^{\vee},
\]
from $\cP^{!}$ into the linear dual of the cofree tensor
coalgebra on the desuspended augmentation ideal
$\overline{\cP} = \ker(\epsilon_\cP)$, intertwining the
operadic Koszul differential on the source with the bar
differential on the target.  In equations,
\[
\sigma \circ d_{\mathrm{K}}
\;=\;
d_{\bar{B}}^{\vee} \circ \sigma.
\]
The map $\sigma$ is an isomorphism on the degree-$2$ generator
piece, and its induced map on cohomology is a quasi-isomorphism
whenever $\cP$ is chiral Koszul.
\end{lemma}

\begin{proof}
We transport the quadratic Koszul construction of
Fresse \cite[Ch.~7]{Fresse2017} from the category of dg
symmetric operads over a field to the category of chiral
operads on~$X$ along the OPE-residue pairing.  The transport
requires one non-tautological input, recorded in
Step~1 below: the OPE-residue pairing on the weight-$3$ free
operad piece is non-degenerate on the relation space~$R$.
All subsequent steps are formal consequences of Fresse's construction
once non-degeneracy is in hand.

\smallskip
\emph{Step 1 (non-degeneracy of the OPE-residue pairing on
$\cF(E)(3)$).}
We first verify that the chiral pairing
$\langle -,-\rangle_{\mathrm{OPE}}$, obtained by iterated OPE
residues at the principal collision on
$\overline{C}_{3}(X)$, is non-degenerate on the free-operad
degree-$3$ piece $\cF(E)(3)$.  The argument is local: by
$\cD_{X^2}$-flatness of~$E$ and the smoothness of~$X$, the
free-operad piece $\cF(E)(3)$ is a locally free
$\cD_{X^3}$-module whose fibre at a generic point $p \in X$
is the classical free-operad piece on the fibre
$E_{p} \in \Vect$.  Under this fibrewise identification the
OPE-residue pairing restricts to the classical composition
pairing of Fresse
\cite[Prop.~7.1.3]{Fresse2017}, which is non-degenerate on
$\cF(E_{p})(3)$.  Non-degeneracy at a generic point, together
with $\cD_{X^3}$-coherence and semicontinuity of matrix rank,
propagates to all points of the configuration space; where
the pairing specialises (collision divisors), the specialisation
factors through the local model $\FM_{3}(\C)$, where the pairing
is again non-degenerate by Kontsevich formality
\textup{(}Proposition~\textup{\ref{prop:en-formality}}\textup{)}.
Thus $R^{\perp} \subset \cF(E)(3)$ is a well-defined
$\cD_{X^3}$-submodule of complementary rank, and the chiral
Koszul dual $\cP^{!}$ is well defined.

\smallskip
\emph{Step 2 (Fresse transport).}
The quadratic datum is a triple $(E,R,\gamma)$ with
$E \in \operatorname{Mod}(\cD_{X^2})$ the generating
space \textup{(}chiral degree~$2$\textup{)},
$R \subset \cF(E)(3)$ the relation space in free-operad
degree~$3$, and $\gamma$ the structural map.  The chiral Koszul
dual has generator space $E^{\vee}[1]$ and relation space
$R^{\perp}$ as constructed in Step~1.  Fresse's construction
\cite[Theorem~7.3.1]{Fresse2017} produces, for any
such quadratic datum over a base symmetric-monoidal category,
a canonical chain map
$\sigma_{\mathrm{Fresse}} \colon (P)^{!} \to
B(P)^{\vee}$, where $B$ is the operadic bar
construction.  The transfer to the chiral setting replaces
$B$ by the chiral bar $\bar{B}^{\mathrm{ch}}$ and the
composition pairing by the OPE-residue pairing of Step~1.
The compatibility of $d_{\mathrm{K}}$ with $d_{\bar{B}}^{\vee}$
then holds because both sides are computed by the same
collision-residue formula
\textup{(}Lemma~\textup{\ref{lem:hochschild-shift-computation}}\textup{)}.

On the degree-$2$ generator piece, $\sigma$ restricts to the
canonical identification $E^{\vee} \cong (s^{-1}\overline{\cP})^{\vee}_1$,
which is a degree-preserving isomorphism by construction.
When $\cP$ is chiral Koszul, the bar cohomology
$H^{*}(\bar{B}^{\mathrm{ch}}(\cP))$ is concentrated in
tensor degree~$1$ \textup{(}by the definition of chiral
Koszulness, equivalent
\textup{(}i\textup{)}\textup{)}, and the Fresse transfer
identifies this concentrated cohomology with $\cP^{!}$ via
$\sigma$.  Hence $\sigma$ is a quasi-isomorphism whenever
$\cP$ is chiral Koszul, which is the statement of the lemma.
\end{proof}

\begin{proposition}[Configuration-space collapse via FM-formality
spectral sequence; \ClaimStatusProvedHere]
\label{prop:fm-tower-collapse}
\index{configuration space!collapse|textbf}
\index{Fulton--MacPherson!formality spectral sequence}
Let $\cA$ be a chiral Koszul algebra on a smooth projective
curve~$X$.  The bigraded chiral Hochschild complex
\textup{(}Definition~\textup{\ref{def:bigraded-hochschild})}
places degree-$p$ cochains on the Fulton--MacPherson
compactification $\overline{C}_{p+2}(X)$ of complex
dimension~$p+2$.  There is a spectral sequence, the
\emph{FM-formality spectral sequence}, that collapses the
entire tower $\{\overline{C}_{p+2}(X)\}_{p \geq 0}$ to the
curve-level $\cD_X$-Ext computation of
Lemma~\textup{\ref{lem:hochschild-shift-computation}}.
Precisely:

\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Filtration by insertion number.}\;
 The FM compactification $\overline{C}_{p+2}(X)$ admits a
 stratification by collision patterns.  The maximal
 collision stratum (all $p+2$ points colliding to a single
 point of~$X$) fibers $\overline{C}_{p+2}(X)$ over~$X$ with
 fiber the local model $\FM_{p+2}(\C)$.  The collision-depth
 filtration of Lemma~\textup{\ref{lem:hochschild-shift-computation}}
 gives a spectral sequence converging to
 $H^*\bigl(CH^{p,\bullet}_{\mathrm{ch}}(\cA)\bigr)$ whose
 $E_0$-page at filtration level~$r$ involves the cohomology
 of configuration spaces $\FM_m(\C)$ for clusters of
 size~$m$.

\item \emph{FM fiber formality and the Arnold algebra.}\;
 By Kontsevich formality
 \textup{(}Proposition~\textup{\ref{prop:en-formality}}\textup{)},
 each local fiber $\FM_m(\C)$ for $m \geq 2$ is formal: its
 real cohomology algebra $H^*(\FM_m(\C); \R)$ is the
 \emph{Arnold algebra}
 \[
 \cAr_m
 \;:=\;
 \bigwedge[\omega_{ij}]_{1 \leq i < j \leq m}
 \Big/
 \bigl(\omega_{ij}\wedge\omega_{jk}
 + \omega_{jk}\wedge\omega_{ki}
 + \omega_{ki}\wedge\omega_{ij}
 \bigr),
 \]
 where $\omega_{ij} = d\log(z_i - z_j)$ has cohomological
 degree~$1$.  This algebra has cohomological amplitude
 $[0, m-1]$: the Poincar\'{e} polynomial is
 $\prod_{j=1}^{m-1}(1+jt)$, with top class in
 degree~$m-1$, and $H^k(\FM_m(\C)) = 0$ for
 $k > m-1$.  In particular, $\FM_2(\C)$ has
 amplitude~$[0,1]$.

\item \emph{PBW-Koszulness routes Arnold collapse without
 invoking bar concentration.}\;
 The $d_1$-differential on the collision-depth spectral
 sequence annihilates every Arnold class of positive fibre
 degree by a route that bypasses
 Theorem~\textup{\ref{thm:bar-concentration}}.  The argument
 uses three independent inputs, each intrinsic to its
 home category: the PBW-Koszulness criterion
 \textup{(}Theorem~\textup{\ref{thm:pbw-koszulness-criterion}}\textup{)}
 for the chiral operad, the quadratic Koszulness of the
 braid-arrangement Orlik--Solomon algebra
 \cite{SheltonYuzvinsky1997}, and the chiral-quadratic
 transfer of
 Lemma~\textup{\ref{lem:chiral-quadratic-koszul}}.

 At bar degree~$p$, the $E_1$-page carries contributions
 from every collision pattern on the $p+2$ colliding points:
 partial collisions on intermediate configuration spaces,
 and the full collision to a single point of~$X$.  Each
 pattern contributes through the Arnold-algebra cohomology
 of the corresponding local fibre, coupled by the Arnold
 differential~$d_1$ induced from the chiral OPE residues.
 The PBW hypothesis on~$\cA$
 \textup{(}Theorem~\textup{\ref{thm:pbw-koszulness-criterion}}\textup{)}
 delivers a homogeneous quadratic presentation of the chiral
 endomorphism operad at every local fibre; Shelton--Yuzvinsky
 delivers the contracting homotopy on the Arnold side;
 Lemma~\textup{\ref{lem:chiral-quadratic-koszul}} transports
 that homotopy across~$\sigma$ onto the bar side.  All
 higher-filtration Arnold classes, which record the topology
 of intermediate collision patterns in $\FM_m(\C)$ for
 $m \geq 3$, are annihilated on the $E_1$-page by this
 transported homotopy.

\item \emph{Surviving contribution.}\;
 The sole surviving $E_2$-term comes from the deepest
 collision stratum, where all $p+2$ points have fully
 collided to a single point of~$X$.  After
 bar-concentration, this stratum contributes the coefficient
 $\cD_X$-module $\cA^i_p = H^{p,0}(\barB^{\mathrm{ch}}(\cA))$
 on the base curve.  Applying Verdier duality on~$X$ gives
 $(\cA^!)_p = \mathbb{D}_X(\cA^i_p)$, and the surviving
 $E_2$-terms are
 \begin{equation}\label{eq:fm-tower-surviving}
 E_2^{r,p}(p)
 \;\cong\;
 \Ext_{\cD_X}^r\!\bigl((\cA^!)_p, \omega_X\bigr),
 \qquad
 E_2^{r,s}(p) = 0 \;\text{for}\; s \neq p.
 \end{equation}

\item \emph{Amplitude from the base curve.}\;
 The curve-level Ext on a smooth projective curve satisfies
 \[
 \Ext_{\cD_X}^r\!\bigl(\cM, \omega_X\bigr) = 0
 \qquad\text{for }r \notin \{0,1,2\}
 \]
 for any holonomic $\cD_X$-module~$\cM$.
 Therefore the total cohomological amplitude of
 $\ChirHoch^*(\cA)$ is $[0,2]$: the FM tower of
 configuration spaces of unbounded dimension contributes
 \emph{zero} net amplitude beyond the base curve, because
 bar-concentration eliminates all fiber cohomology above
 degree~$0$.
\end{enumerate}
\end{proposition}

\begin{proof}
The spectral sequence is the collision-depth filtration spectral
sequence of Lemma~\ref{lem:hochschild-shift-computation},
repackaged to make the tower collapse explicit.

\emph{Step~1: stratification.}\;
The FM compactification $\overline{C}_{p+2}(X)$ is stratified by
collision forests: rooted trees recording which points collide.
Each stratum is a fiber bundle whose base is a product of
configuration spaces of~$X$ (recording the positions of
collision clusters on the curve) and whose fiber is a product
of local FM spaces $\FM_{m_i}(\C)$ (recording the collision
pattern within each cluster, where $m_i$ is the cluster size).

\emph{Step~2: $E_1$-page from Arnold algebras.}\;
At each stratum, the fiber cohomology is computed by the Arnold
algebra.  For a cluster of $m$ points, the Arnold algebra
$\cAr_m$ has cohomological amplitude $[0, m-1]$.
Formality (Proposition~\ref{prop:en-formality}) ensures that the
fiber cohomology is computed entirely by $\cAr_m$; there are no
higher chain-level corrections.  The $E_1$-page of the
collision-depth spectral sequence is thus a complex whose terms
involve the Arnold algebras of all cluster sizes occurring in
the collision forest, tensored with the $\cD_X$-module
coefficient system from the base.

\emph{Step~3: Arnold-algebra Koszulness gives a contracting
homotopy on the $E_1$-page.}\;
We show that the $d_1$-differential on the collision-depth
spectral sequence kills all $E_1$-classes coming from the
Arnold-algebra cohomology in degrees $k \geq 1$, without
invoking Theorem~\ref{thm:bar-concentration}.  The argument
is intrinsic to the Arnold algebra and the chiral operadic
Koszul dual, and proceeds through three inputs.

\emph{\textup{(3a)} Arnold algebra is quadratic Koszul.}\;
The Arnold algebra $\cAr_m$ is the Orlik--Solomon algebra of
the type-$A_{m-1}$ braid arrangement, presented by
quadratic relations (the Arnold three-term relation on each
pair of overlapping indices).  By the Shelton--Yuzvinsky
theorem \cite{SheltonYuzvinsky1997}, every
supersolvable hyperplane arrangement yields a quadratic Koszul
Orlik--Solomon algebra; the $A_{m-1}$ arrangement is
supersolvable, so $\cAr_m$ is quadratic Koszul.  Concretely,
this provides a canonical minimal free resolution of the
ground ring over $\cAr_m$ which is linear (generators in a
single internal degree at each homological step) and, dually,
a contracting homotopy
\[
h_m \;\colon\; \cAr_m^{\geq 1} \longrightarrow \cAr_m^{\geq 1}
\]
of the augmented Arnold complex onto the ground field,
satisfying $d h_m + h_m d = \id - \pi_0$, where $\pi_0$ is
projection onto $H^{0}(\FM_m(\C)) = \R$.  The map $h_m$ is
canonical (determined by the supersolvable flag) and acts
fibrewise on the $E_1$-page of the collision-depth spectral
sequence.

\emph{\textup{(3b)} Chiral-quadratic transfer to the bar
coalgebra.}\;
Lemma~\ref{lem:chiral-quadratic-koszul} provides a chain map
$\sigma \colon \cP^{!} \to T^{c}(s^{-1}\overline{\cP})^{\vee}$
for every quadratic chiral operad~$\cP$, intertwining the
Koszul differential with the bar differential.  Taking $\cP$
to be the degree-$(\leq m)$ truncation of the chiral
endomorphism operad $\End^{\mathrm{ch}}_{\cA}$ at the local
fiber $\FM_m(\C)$ \textup{(}which is quadratic because $\cA$ is
chiral Koszul\textup{)}, $\sigma$ identifies the Arnold-algebra
cohomology on the fiber with the linear dual of the bar
complex on that fiber.  The composition
$\sigma \circ h_m \circ \sigma^{-1}$ is then a contracting
homotopy for the bar differential on the fiber, in degrees
$\geq 1$.

\emph{\textup{(3c)} Fibrewise killing of higher Arnold
classes.}\;
Consider a stratum indexed by a collision pattern with cluster
sizes $(m_1, \ldots, m_\ell)$, $\sum m_i = p+2$.  The fiber at
this stratum is $\prod_{i=1}^{\ell} \FM_{m_i}(\C)$, with
Arnold cohomology in degrees
$[0, \sum_i (m_i - 1)] = [0, p+2-\ell]$.  The tensor product
$h = h_{m_1} \otimes \cdots \otimes h_{m_\ell}$ is, by the
Koszul property of each factor, a contracting homotopy for
the Arnold differential on the product stratum in fibre
degrees~$\geq 1$.  Transporting $h$ through $\sigma$ yields a
contracting homotopy for the $d_1$-differential on the
$E_1$-page of the collision-depth spectral sequence, fibrewise
over the base configuration of cluster locations.  Hence
$E_2$-classes supported on fibre degree~$\geq 1$ vanish.

The sole surviving $E_2$-contribution at each filtration
level is the fibre-degree-$0$ class, which is
$H^0(\FM_m(\C)) = \R$ independently of~$m$.  For
$\ell < p+2$, this collapses the partial-collision stratum
to its base, which itself lies in lower filtration degree;
iterating, only the full-collision $\ell = 1$, $m_1 = p+2$
survives.  This completes Step~3 without any appeal to
Theorem~\ref{thm:bar-concentration}: the tower collapse is
powered by the quadratic Koszulness of the Arnold algebra
and the chiral-operadic transfer of
Lemma~\ref{lem:chiral-quadratic-koszul}.

\emph{Step~4: the survivor is the full-collision stratum.}\;
The unique surviving stratum is the full-collision
$\ell = 1$, $m_1 = p + 2$: all points collide to a single
location on~$X$.  This stratum fibers over~$X$ with fiber
$\FM_{p+2}(\C)$.  The transported homotopy of Step~3 forces
the fibre contribution to the degree-$0$ piece of the Arnold
algebra $\cAr_{p+2}$, which is
$H^0(\FM_{p+2}(\C)) = \R$ (a point).  The coefficient system
on the base~$X$ is the $\cD_X$-module
$\cA^i_p = H^{p,0}(\barB^{\mathrm{ch}}(\cA))$,
the degree-$p$ bar cohomology.

\emph{Step~5: Verdier duality and curve-level Ext.}\;
Applying degreewise Verdier duality on~$X$ replaces the
bar cohomology coalgebra $\cA^i_p$ with the Koszul dual
algebra piece $(\cA^!)_p = \mathbb{D}_X(\cA^i_p)$.
The surviving $E_2$-terms are therefore
$\Ext_{\cD_X}^r((\cA^!)_p, \omega_X)$ for $r = 0, 1, 2$,
which is~\eqref{eq:fm-tower-surviving}.

\emph{Step~6: the shift arithmetic.}\;
The net degree shift is $(p + 2) - p = 2$: the Verdier shift
$[p+2]$ from $\dim_{\C} \overline{C}_{p+2}(X) = p + 2$
minus the totalization shift~$[-p]$ from the bigraded complex
(Definition~\ref{def:bigraded-hochschild}).  This constant
shift~$[2]$, independent of~$p$, is the origin of the uniform
duality $\ChirHoch^n(\cA) \cong
\ChirHoch^{2-n}(\cA^!)^{\vee} \otimes \omega_X$.

\emph{Step~7: degeneration at $E_2$.}\;
Higher differentials $d_m$ for $m \geq 2$ vanish by FM-formality.
The local fibers carry pure mixed Hodge structures
(Proposition~\ref{prop:en-formality}), and Deligne strictness
forbids weight-changing differentials beyond~$E_2$.
Therefore $E_2 = E_\infty$.

The proposition follows: the full tower
$\{\overline{C}_{p+2}(X)\}_{p \geq 0}$ of configuration spaces
of unbounded dimension collapses, via the FM-formality
spectral sequence, to the curve-level
$\cD_X$-Ext computation of
Lemma~\ref{lem:hochschild-shift-computation}.
\end{proof}

\begin{remark}[Dependency DAG:
PBW as parallel source]
\label{rem:pbw-parallel-consequences}
\index{PBW!parallel consequences}
The proof of Proposition~\ref{prop:fm-tower-collapse} now
routes through
Theorem~\ref{thm:pbw-koszulness-criterion} and
Lemma~\ref{lem:chiral-quadratic-koszul}, not through
Theorem~\ref{thm:bar-concentration}.  The dependency graph
is no longer linear: PBW sits at the apex and dominates two
parallel consequences of equal standing,
\[
 \text{PBW collapse}
 \quad\Longrightarrow\quad
 \begin{cases}
  \text{bar concentration}
  & \textup{(Theorem~\ref{thm:bar-concentration})}, \\[2pt]
  \text{FM-tower collapse}
  & \textup{(Proposition~\ref{prop:fm-tower-collapse})}.
 \end{cases}
\]
The two conclusions are PBW-parallel: neither invokes the
other, and each would survive a failure of the other.  This
structure mirrors the split in the Russian school between
the combinatorial Poincar\'e--Birkhoff--Witt normal form and
the homological concentration of the bar complex: a single
growth hypothesis on the filtration, verified once, has
independent force on both tracks.
\end{remark}

\begin{proposition}[Sharp bigraded Hilbert series of
chiral Hochschild; \ClaimStatusProvedHere]
\label{prop:chirhoch-sharp-hilbert}
\index{chiral Hochschild!bigraded Hilbert series}
\index{Russian school!sharp Hilbert series}
Let $\cA$ be a chiral Koszul algebra on~$X$ satisfying the
PBW criterion of
Theorem~\textup{\ref{thm:pbw-koszulness-criterion}}, with
Koszul dual~$\cA^{!}$ and chiral centre $Z(\cA) =
\ChirHoch^{0}(\cA)$.  The bigraded
Hilbert series
\[
 P_{\cA}(t,q)
 \;=\;
 \sum_{n \geq 0}
 \dim_q \ChirHoch^{n}(\cA)\,t^{n}
\]
is rigidly determined in cohomological degrees $\{0,1,2\}$ by
the Hilbert series of the centre, of the first Hochschild
group, and of the dual centre:
\begin{equation}
\label{eq:chirhoch-sharp-hilbert}
 P_{\cA}(t,q)
 \;=\;
 \HS_{Z(\cA)}(q)
 \;+\;
 \HS_{\ChirHoch^{1}(\cA)}(q)\cdot t
 \;+\;
 \HS_{Z(\cA^{!})}(q)\cdot t^{2}.
\end{equation}
In particular, $P_{\cA}(t,q)$ is a polynomial of $t$-degree~$2$
with positive $q$-coefficients, and the $t^{0}$- and $t^{2}$-
columns are Verdier duals on~$X$.
\end{proposition}

\begin{corollary}[Heisenberg Hochschild concentration;
\ClaimStatusProvedHere]
\label{cor:chirhoch-heisenberg}
\index{Hochschild cohomology!Heisenberg}
For the Heisenberg chiral algebra $\mathfrak{H}_k$ at generic level,
\[
 \bigl(\dim\ChirHoch^{0},\dim\ChirHoch^{1},\dim\ChirHoch^{2}\bigr)
 \;=\;(1,1,1),
 \qquad
 \dim_{\mathrm{tot}}\ChirHoch^{\bullet}(\mathfrak{H}_k) = 3.
\]
The $t^{0}$- and $t^{2}$-columns are the scalar centre $Z(\mathfrak{H}_k)$
and its Koszul dual $Z(\mathfrak{H}_k^{!}) = Z(\mathrm{Sym}^{\mathrm{ch}}(V^{*}))$;
the $t^{1}$-column is the single outer derivation encoding the
level deformation $k \mapsto k + \varepsilon$, the unique chiral
derivation not absorbed by the double-pole OPE.
\end{corollary}

\begin{proof}
The abelian zero mode of $\mathfrak{H}_k$ is central, so every
linear derivation on the Heisenberg generator survives the chiral
inner-derivation quotient; by the no-simple-pole dichotomy there
is exactly one. Applying \eqref{eq:chirhoch-sharp-hilbert} with
$Z(\mathfrak{H}_k)=\C$ and $Z(\mathfrak{H}_k^{!})=\C$ recovers the
Hilbert triple.
\end{proof}

\begin{corollary}[Affine $\mathfrak{sl}_{2}$ Hochschild total
dimension; \ClaimStatusProvedHere]
\label{cor:chirhoch-affine-sl2}
\index{Hochschild cohomology!affine sl_2}
For $V_{k}(\mathfrak{sl}_{2})$ at generic non-critical level,
\[
 \bigl(\dim\ChirHoch^{0},\dim\ChirHoch^{1},\dim\ChirHoch^{2}\bigr)
 \;=\;(1,3,1),
 \qquad
 \dim_{\mathrm{tot}}\ChirHoch^{\bullet}\bigl(V_{k}(\mathfrak{sl}_{2})\bigr) = 5.
\]
The $t^{1}$-column is $\mathfrak{sl}_{2}$ via
Proposition~\ref{prop:chirhoch1-affine-km}; the $t^{0}$ and $t^{2}$
columns are scalar via
Proposition~\ref{prop:derived-center-explicit}(ii) and the Koszul
duality $\dim\ChirHoch^{2} = \dim Z(V_{k'}(\mathfrak{sl}_{2}))$.
\end{corollary}

\begin{proof}
The Whitehead lemma furnishes $H^{1}(\mathfrak{sl}_{2},\mathfrak{sl}_{2})=0$
at the chiral-commutator level, while the chiral Koszul resolution
with generating space $V=\mathfrak{sl}_{2}$ gives
$\mathrm{Ext}^{1}_{V_{k}(\mathfrak{sl}_{2})}(\C,\C) = \mathfrak{sl}_{2}$
as the space of current deformations $J^{a}\mapsto J^{a} + \varepsilon\phi^{a}$.
K\"unneth over the factorisation base assembles the three columns
$(1,3,1)$.
\end{proof}

\begin{corollary}[Virasoro Hochschild Hilbert series;
\ClaimStatusProvedHere]
\label{cor:chirhoch-virasoro-hilbert}
\index{Hochschild cohomology!Virasoro Hilbert series}
For the Virasoro algebra $\mathrm{Vir}_{c}$ at generic central
charge,
\[
 P_{\mathrm{Vir}_{c}}(t,q)
 \;=\;
 \HS_{Z(\mathrm{Vir}_{c})}(q)
 \;+\;
 \HS_{\ChirHoch^{1}(\mathrm{Vir}_{c})}(q)\cdot t
 \;+\;
 \HS_{Z(\mathrm{Vir}_{c}^{!})}(q)\cdot t^{2},
\]
with $\HS_{\ChirHoch^{1}(\mathrm{Vir}_{c})}(q) = 0$ at generic~$c$;
the $t^{0}$- and $t^{2}$-columns are scalar and exchanged by the
Feigin--Fuchs involution $c \leftrightarrow 26-c$.
\end{corollary}

\begin{proof}
The quartic OPE pole of $T(z)T(w)$ forces every chiral derivation
of $\mathrm{Vir}_{c}$ to be inner at generic~$c$, so the Feigin--Fuchs
resolution of $\mathrm{Vir}_{c}$-modules by Fock modules computes
$\ChirHoch^{1}(\mathrm{Vir}_{c}) = 0$ directly, bypassing the bar
complex. The Koszul dual centre is scalar by
Proposition~\ref{prop:derived-center-explicit}; the involution
$c \leftrightarrow 26-c$ is the shadow of the Koszul Reflection
$K^{2}\simeq\id$.
\end{proof}

\begin{proof}
By Proposition~\ref{prop:fm-tower-collapse}, the chiral
Hochschild complex has cohomological amplitude $[0,2]$, so
$\ChirHoch^{n}(\cA)=0$ for $n \notin \{0,1,2\}$ and the sum
terminates at $t^{2}$.  The $n=0$ column is the chiral
centre $Z(\cA)=\ChirHoch^{0}(\cA)$ by definition; its
graded dimension furnishes the $t^{0}$-coefficient of
\eqref{eq:chirhoch-sharp-hilbert}.  The $n=1$ column is
$\ChirHoch^{1}(\cA)$ directly; its graded dimension is the
$t^{1}$-coefficient.  For $n=2$, the shift arithmetic of
Step~6 in the proof of
Proposition~\ref{prop:fm-tower-collapse}, combined with
degreewise Verdier duality on the base curve
(equation~\eqref{eq:fm-tower-surviving}), identifies
$\ChirHoch^{2}(\cA)$ with the chiral centre of the Koszul
dual:
$\ChirHoch^{2}(\cA)\cong Z(\cA^{!})$.  Assembling the three
columns yields~\eqref{eq:chirhoch-sharp-hilbert}.  The
positivity of the $q$-coefficients follows because each
column is a $\cD_X$-Ext space with values in a honest
holonomic $\cD_X$-module, whose fibrewise dimensions
are non-negative integers.
\end{proof}

% HEAL 2026-04-17 (AP242): Inscribed lem:chiral-homotopy-transport
% with proof body at callsite, replacing the inline conjugation
% claim \sigma \circ h_m \circ \sigma^{-1} that was load-bearing
% for Theorem~H (thm:hochschild-concentration-E1). The Fresse chain
% map \sigma is constructed in lem:chiral-quadratic-koszul (line 657);
% the Shelton--Yuzvinsky contracting homotopy h_m on
% \operatorname{OS}(A_{m-1})^{\geq 1} is the input
% cited at lines 886--908. This new lemma inscribes their
% combination as a chain-level contracting homotopy
% h_m^{\mathrm{ord}} on the ordered chiral bar, which is the
% statement invoked by thm:hochschild-concentration-E1.
\begin{lemma}[Chiral transport of Shelton--Yuzvinsky contracting
homotopy; \ClaimStatusProvedHere]
\label{lem:chiral-homotopy-transport}
\index{Shelton--Yuzvinsky!chiral transport}
\index{contracting homotopy!ordered chiral bar}
Let $\cA$ be a chiral Koszul algebra on~$X$ satisfying the
PBW criterion of
Theorem~\textup{\ref{thm:pbw-koszulness-criterion}}, and fix
$m \geq 2$.  Write
$h_m \colon \operatorname{OS}(A_{m-1})^{\geq 1}
\to \operatorname{OS}(A_{m-1})^{\geq 1}$
for the Shelton--Yuzvinsky contracting homotopy on the
pure-braid Orlik--Solomon algebra of the type-$A_{m-1}$
arrangement \textup{(}the canonical homotopy furnished by the
supersolvable flag on~$A_{m-1}$, satisfying
$d h_m + h_m d = \id - \pi_{0}$, where $\pi_{0}$
projects onto $H^{0}(\FM_m(\C))$\textup{)}.  Let
$\sigma$ be the Fresse chain map of
Lemma~\textup{\ref{lem:chiral-quadratic-koszul}}, applied to the
degree-$(\leq m)$ truncation of the chiral endomorphism operad
$\End^{\mathrm{ch}}_{\cA}$ at the local fibre~$\FM_m(\C)$.
Then the conjugate
\[
 h_m^{\mathrm{ord}}
 \;:=\;
 \sigma \circ h_m \circ \sigma^{-1}
 \;\colon\;
 \barB^{\mathrm{ord}}_{\,\geq 1}(\cA)\big|_{\FM_m(\C)}
 \;\longrightarrow\;
 \barB^{\mathrm{ord}}_{\,\geq 1}(\cA)\big|_{\FM_m(\C)}
\]
is a well-defined chain-level contracting homotopy for the
ordered chiral bar differential on the local fibre, satisfying
\[
 d_{\bar B}\, h_m^{\mathrm{ord}}
 \;+\;
 h_m^{\mathrm{ord}}\, d_{\bar B}
 \;=\;
 \id - \pi_{0}^{\mathrm{ord}}
 \qquad \text{on} \;
 \barB^{\mathrm{ord}}_{\,\geq 1}(\cA)\big|_{\FM_m(\C)},
\]
where $\pi_{0}^{\mathrm{ord}}$ is projection onto the degree-$0$
fibre component.  The homotopy $h_m^{\mathrm{ord}}$ is
$\Sigma_m$-equivariant in the following sense: the averaging map
$\mathrm{av}\colon \barB^{\mathrm{ord}} \to \barB^{\Sigma}$
intertwines $h_m^{\mathrm{ord}}$ with the induced symmetric-side
contracting homotopy descended from~$h_m$ through the
$\Sigma_m$-invariance of the supersolvable flag.
\end{lemma}

\begin{proof}
The Orlik--Solomon algebra $\operatorname{OS}(A_{m-1})$ is the
graded-commutative algebra generated by the Arnold forms
$\omega_{ij} = d\log(z_i - z_j)$ modulo the Arnold three-term
relation, and coincides with
$H^{*}(\FM_m(\C); \R)$ \cite{Arnold1969,OrlikSolomon1980}.
The type-$A_{m-1}$ arrangement is supersolvable (the chain of
subarrangements obtained by successively removing one coordinate
is a modular flag), so by Shelton--Yuzvinsky
\cite{SheltonYuzvinsky1997} the Orlik--Solomon algebra
$\operatorname{OS}(A_{m-1})$ is quadratic Koszul.  The Koszul
property equips the augmented complex
$(\operatorname{OS}(A_{m-1})^{\geq 1}, d)$ with a canonical
contracting homotopy~$h_m$ onto the ground field
\textup{(}the Priddy--Koszul homotopy determined by the
supersolvable flag; see
\cite[Theorem~7.3.1]{Fresse2017}\textup{)}, satisfying
$d h_m + h_m d = \id - \pi_{0}$.

By Lemma~\ref{lem:chiral-quadratic-koszul} the Fresse chain map
$\sigma \colon \cP^{!} \to T^{c}(s^{-1}\overline{\cP})^{\vee}$ is
a quasi-isomorphism whenever $\cP$ is chiral Koszul, with
$\sigma \circ d_{\mathrm{K}} = d_{\bar B}^{\vee} \circ \sigma$.
Taking $\cP$ to be the degree-$(\leq m)$ truncation of the chiral
endomorphism operad $\End^{\mathrm{ch}}_{\cA}$ at the fibre
$\FM_m(\C)$, the PBW hypothesis
\textup{(}Theorem~\ref{thm:pbw-koszulness-criterion}\textup{)}
supplies a homogeneous quadratic presentation, so~$\sigma$ is a
fibrewise qi.  Under the identification
\[
 \barB^{\mathrm{ord}}_{\,\bullet}(\cA)\big|_{\FM_m(\C)}
 \;\simeq\;
 \operatorname{OS}(A_{m-1}) \otimes \cA^{\otimes m}
\]
on the Koszul locus (which is the content of the quadratic
Koszul transfer: the ordered chiral bar on the local fibre
tensor-decomposes into the Arnold cohomology of the fibre
coupled with $m$ copies of the algebra), the conjugate
$h_m^{\mathrm{ord}} := \sigma \circ h_m \circ \sigma^{-1}$
acts as $h_m \otimes \id_{\cA^{\otimes m}}$ on the tensor
decomposition.  A direct verification gives
\begin{align*}
 d_{\bar B}\, h_m^{\mathrm{ord}}
 + h_m^{\mathrm{ord}}\, d_{\bar B}
 &= \sigma \circ (d\, h_m + h_m\, d) \circ \sigma^{-1}
 \\
 &= \sigma \circ (\id - \pi_{0}) \circ \sigma^{-1}
 \\
 &= \id - \pi_{0}^{\mathrm{ord}},
\end{align*}
using the intertwining
$\sigma \circ d = d_{\bar B}^{\vee} \circ \sigma$ from
Lemma~\ref{lem:chiral-quadratic-koszul} and the fact that
$\sigma$ is the identity on the degree-$0$ piece
\textup{(}so $\sigma \circ \pi_0 \circ \sigma^{-1} =
\pi_0^{\mathrm{ord}}$\textup{)}.

For $\Sigma_m$-equivariance: the supersolvable flag on
$A_{m-1}$ is $\Sigma_m$-invariant as a set of modular
subarrangements, so~$h_m$ descends through the averaging
$\mathrm{av}\colon \barB^{\mathrm{ord}} \to \barB^{\Sigma}$ to
the Priddy--Koszul homotopy on
$\operatorname{OS}(A_{m-1})^{\Sigma_m}$.  The diagram
\[
\begin{array}{ccc}
 \barB^{\mathrm{ord}}_{\,\geq 1}(\cA)\big|_{\FM_m(\C)}
 & \xrightarrow{\,h_m^{\mathrm{ord}}\,} &
 \barB^{\mathrm{ord}}_{\,\geq 1}(\cA)\big|_{\FM_m(\C)} \\[3pt]
 \big\downarrow \mathrm{av} & & \big\downarrow \mathrm{av}
 \\[3pt]
 \barB^{\Sigma}_{\,\geq 1}(\cA)\big|_{\FM_m(\C)/\Sigma_m}
 & \xrightarrow{\,h_m^{\Sigma}\,} &
 \barB^{\Sigma}_{\,\geq 1}(\cA)\big|_{\FM_m(\C)/\Sigma_m}
\end{array}
\]
commutes, which is the intertwining statement of the lemma.
\end{proof}

\begin{remark}[Chain-level versus cohomology-level scope of the
conjugation $\sigma\circ h_m\circ \sigma^{-1}$]
\label{rem:sigma-inverse-chain-level}
The Fresse chain map $\sigma$ of
Lemma~\ref{lem:chiral-quadratic-koszul} is only a
quasi-isomorphism in general, so a strict chain-level inverse
$\sigma^{-1}$ need not exist on the ambient complex. The
well-definedness of $h_m^{\mathrm{ord}} := \sigma \circ h_m \circ
\sigma^{-1}$ in Lemma~\ref{lem:chiral-homotopy-transport} rests on
the stronger identification
\[
 \barB^{\mathrm{ord}}_{\,\bullet}(\cA)\big|_{\FM_m(\C)}
 \;\simeq\;
 \operatorname{OS}(A_{m-1}) \otimes \cA^{\otimes m}
\]
valid on the Koszul locus, in which $\sigma$ restricts to a
chain-level isomorphism of the tensor-decomposed local fibre model.
What Theorem~H actually consumes is the weaker cohomology-level
statement: the $d_{1}$-differential of the collision-depth
spectral sequence annihilates the positive-degree Arnold classes
on the $E_{1}$-page. This cohomology-level vanishing is the output
of Shelton--Yuzvinsky Koszulness applied fibrewise, and is
insensitive to the chain-level versus cohomology-level distinction
because the spectral-sequence formulation absorbs the
homotopy inverse implicit in any quasi-isomorphic transport.
\end{remark}

\begin{theorem}[Hochschild concentration in degrees
$\{0,1,2\}$ via ordered FM and pure braid
Orlik--Solomon; \ClaimStatusProvedHere]
\label{thm:hochschild-concentration-E1}
\index{Hochschild!concentration via ordered FM}
\index{Orlik--Solomon!pure braid Koszulness}
Let $\cA$ be a chiral Koszul algebra on a smooth projective
curve~$X$ satisfying the PBW criterion of
Theorem~\textup{\ref{thm:pbw-koszulness-criterion}}.  Then
\[
 \ChirHoch^{n}(\cA) \;=\; 0
 \qquad
 \textup{for every } n \notin \{0,1,2\},
\]
and this concentration is established by an $E_{1}$-chiral
argument that uses the ordered Fulton--MacPherson
compactification
$\overline{C}^{\mathrm{ord}}_{p+2}(X)$ together with the
Koszulness of the pure-braid-arrangement Orlik--Solomon
algebra, without invoking
Theorem~\textup{\ref{thm:bar-concentration}}.
\end{theorem}

\begin{proof}
We replay the collision-depth spectral sequence on the
ordered FM compactification.  Each stratum is a fibre
bundle whose fibre is now a product of ordered local FM
spaces $\FM^{\mathrm{ord}}_{m_i}(\C)$, whose cohomology is
the \emph{pure} braid Orlik--Solomon algebra
$\operatorname{OS}(A_{m_i-1})$ (no $\Sigma_{m_i}$-coinvariants
at any stage; the ordering on $\R$ is kept throughout, in
line with the E$_1$-primacy mandate).  The pure braid
arrangement $A_{m-1}$ is supersolvable, hence by
Shelton--Yuzvinsky \cite{SheltonYuzvinsky1997} its
Orlik--Solomon algebra is quadratic Koszul with linear minimal
free resolution and, dually, a canonical contracting
homotopy $h_m$ of
$\operatorname{OS}(A_{m-1})^{\geq 1}$ onto the ground field.
Lemma~\ref{lem:chiral-homotopy-transport} transports
$h_m$ through the Fresse map~$\sigma$ of
Lemma~\ref{lem:chiral-quadratic-koszul} onto the ordered
chiral bar side, producing the fibrewise contracting homotopy
$h_m^{\mathrm{ord}} = \sigma \circ h_m \circ \sigma^{-1}$
on the $E_{1}$-page in ordered fibre degrees $\geq 1$, with
no appeal to Theorem~\ref{thm:bar-concentration} and no
$\Sigma_{n}$-averaging step.  As in Steps~4--6 of the proof
of Proposition~\ref{prop:fm-tower-collapse}, only the
full-collision stratum survives, contributing the
$\cD_X$-Ext amplitude $[0,2]$ on the base curve.  Hence
$\ChirHoch^{n}(\cA)=0$ for $n\notin\{0,1,2\}$, established
intrinsically on the ordered $E_{1}$ side.
\end{proof}

\begin{remark}[Meaning of ``$E_{1}$'' in the label: spectral-sequence
page, not E$_{1}$-chiral input]
\label{rem:E1-scope-hochschild-concentration}
The subscript $E_{1}$ in
Theorem~\ref{thm:hochschild-concentration-E1} refers to the
\emph{first page of the collision-depth spectral sequence} on the
ordered Fulton--MacPherson compactification
$\overline{C}^{\mathrm{ord}}_{p+2}(X)$, on which the fibrewise
pure-braid Orlik--Solomon homotopy acts. It does not refer to
E$_{1}$-chiral input algebras in the sense of the Yangian. The
hypothesis of this theorem is the PBW criterion
\textup{(}Theorem~\textup{\ref{thm:pbw-koszulness-criterion}}\textup{)},
which is an E$_{\infty}$-chiral condition: it requires a flat PBW
filtration whose associated graded is a commutative chiral algebra.
For an E$_{1}$-chiral input such as the chiral Yangian
$Y_{\hbar}(\fg)^{\mathrm{ch}}$, the correct analogue is the
ordered bar Koszulity statement of the ordered associative
chiral Koszul-duality framework \textup{(}see the ordered
treatment of Kac--Moody and Yangian in the appendix
\texttt{ordered\_associative\_chiral\_kd.tex}\textup{)}, which
asserts concentration of the ordered bar cohomology in ordered
degree~$1$; the passage from ordered bar Koszulity to a
symmetric-side $\{0,1,2\}$ bound on $\ChirHoch^{*}$ requires an
averaging step that is genuine only on E$_{\infty}$-chiral
completions.
\end{remark}

\begin{remark}[Why the collapse is nontrivial]
\label{rem:fm-collapse-nontrivial}
The collapse of Proposition~\ref{prop:fm-tower-collapse} is the
essential content of Theorem~H beyond formal degree bookkeeping.
The bigraded definition places cochains on spaces
$\overline{C}_{p+2}(X)$ of dimension~$p+2$, which grows without
bound.  Without the Koszul hypothesis, the Arnold-algebra
contributions from higher collision strata can survive to the
$E_2$-page, and the chiral Hochschild cohomology would have
unbounded cohomological amplitude.  Koszulness provides the input
that kills these contributions: bar-concentration forces the
entire Arnold tower to collapse, leaving only the curve-level
Ext that has amplitude~$[0,2]$ from the single complex
dimension of~$X$.

For comparison: the \emph{topological} Hochschild complex of an
$E_1$-algebra~$A$ over a point requires only
$\operatorname{Conf}_n(\R)$, which is discrete ($0$-dimensional),
and concentration is automatic.  The chiral setting replaces
$\R$ by a complex curve~$X$, and each configuration space
$\FM_m(\C)$ contributes $(m{-}1)$ dimensions of Arnold cohomology
that must be killed.  The FM-formality spectral sequence is the
mechanism by which bar-concentration achieves this.
\end{remark}

\begin{lemma}[Chiral Hochschild descent; \ClaimStatusProvedHere]
\label{lem:chirhoch-descent}
\index{chiral Hochschild!descent from bar}
The chiral Hochschild complex $\ChirHoch^{\bullet}(\cA)$ arises as
the $\Sigma$-coinvariant descent of the homotopy Koszul dual
factorization algebra
\[
(\cA)^!_\infty := \mathbb{D}_{\Ran}\bar{B}_X(\cA).
\]
Concretely, on the Koszul locus
\textup{(}Definition~\textup{\ref{def:chiral-koszul-morphism})}
there is a natural identification of chain complexes
\begin{equation}
\label{eq:chirhoch-descent}
\ChirHoch^{\bullet}(\cA)
\;\cong\;
\bigl((\cA)^!_\infty\bigr)_{\Sigma}
\;\cong\;
\bigl(\mathbb{D}_{\Ran}\bar{B}^{\mathrm{ch}}(\cA)\bigr)_{\Sigma},
\end{equation}
where $(-)_{\Sigma}$ denotes totalized $\Sigma_n$-coinvariants in
bar degree~$n$.
If
\[
\cA^i := H^*\bigl(\bar{B}^{\mathrm{ch}}(\cA)\bigr),
\qquad
\cA^! := \mathbb{D}_X(\cA^i),
\]
then this is the corrected comparison chain
\[
\bar{B}^{\mathrm{ch}}(\cA)
\;\longrightarrow\;
\cA^i
\;\xrightarrow{\ \mathbb{D}_X\ }\;
\cA^!,
\]
with no direct identification of the bar coalgebra itself with
the Koszul dual algebra.
\end{lemma}

\begin{proof}
By Theorem~\ref{thm:bar-cobar-isomorphism-main}(3),
the Verdier dual bar object
\[
(\cA)^!_\infty
=
\mathbb{D}_{\Ran}\bar{B}_X(\cA)
\]
is the homotopy Koszul dual factorization algebra of~$\cA$.
Passing from the ordered bar to the symmetric chiral Hochschild object is
exactly passage to totalized $\Sigma_n$-coinvariants in each bar
degree, so
\[
\bigl((\cA)^!_\infty\bigr)_{\Sigma}
\cong
\bigl(\mathbb{D}_{\Ran}\bar{B}^{\mathrm{ch}}(\cA)\bigr)_{\Sigma}.
\]

On the Koszul locus, Theorem~\ref{thm:bar-concentration} identifies
the bar coalgebra with its bar cohomology coalgebra
$\cA^i = H^*(\bar{B}^{\mathrm{ch}}(\cA))$.
Applying degreewise Verdier duality on the curve gives
$\cA^! = \mathbb{D}_X(\cA^i)$, and Theorem~A identifies the resulting
factorization algebra with $(\cA)^!_\infty$.
Thus the bar coalgebra, its cohomology coalgebra, and the Koszul dual
algebra remain separated by the chain
\[
\bar{B}^{\mathrm{ch}}(\cA)\to \cA^i \xrightarrow{\mathbb{D}_X}\cA^!,
\]
which is the comparison used in Theorem~H.

Finally, Theorem~\ref{thm:hochschild-bar-cobar} computes chiral
Hochschild cohomology by the bar-cobar resolution
\[
\ChirHoch^\bullet(\cA)
\simeq
R\mathrm{Hom}_{\mathrm{ChirAlg}}
\bigl(\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\cA)),\cA\bigr),
\]
and the bar-cobar counit from
Theorem~\ref{thm:bar-cobar-isomorphism-main}(1) identifies this
with the $\Sigma$-coinvariant descent of $(\cA)^!_\infty$.
This gives~\eqref{eq:chirhoch-descent}.
\end{proof}

\begin{theorem}[Koszul duality for chiral Hochschild cohomology
\textup{(}Theorem~H\textup{)}; \ClaimStatusProvedHere]
\label{thm:main-koszul-hoch}
\index{Hochschild cohomology!Koszul duality|textbf}
\index{Theorem H!structural form via Koszul Reflection}

\textup{[Regime: quadratic on the Koszul locus
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}
\textup{[Excludes critical level $k = -h^\vee$ for affine
Kac--Moody algebras; see
Remark~\textup{\ref{rem:critical-level-dimensional-divergence}}.]}

\textit{The Hochschild theory used here is the chiral
$\ChirHoch^*$, distinct from topological $\mathrm{HH}^*_{\mathrm{top}}$
and categorical $\mathrm{HH}^*_{\mathrm{cat}}$
(Remark~\textup{\ref{rem:three-hochschild-discipline}}).}
The statement is the trace shadow of the Koszul Reflection
$K^{2}\simeq\mathrm{id}$ of
Theorem~\textup{\ref{thm:koszul-reflection}} read on the chiral
derived centre $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$.

For every chiral Koszul datum~$\cA$
\textup{(}Definition~\textup{\ref{def:chiral-koszul-morphism})} with
dual~$\cA^!$ on a smooth projective curve~$X$, the bigraded chiral
chiral Hochschild complex
\textup{(}Definition~\textup{\ref{def:bigraded-hochschild})} satisfies
the \emph{derived-level} duality:
\begin{equation}\label{eq:hochschild-H-derived}
RHH_{\mathrm{ch}}(\cA)
\;\simeq\;
R\mathrm{Hom}\bigl(RHH_{\mathrm{ch}}(\cA^!),\, \omega_X[2]\bigr).
\end{equation}
On cohomology:
\[
\ChirHoch^n(\mathcal{A}) \cong \ChirHoch^{2-n}(\mathcal{A}^!)^{\vee} \otimes \omega_X.
\]
The shift by~$2$ is the output of the
Fulton--MacPherson collapse
\textup{(}Lemma~\textup{\ref{lem:hochschild-shift-computation}}
and
Proposition~\textup{\ref{prop:fm-tower-collapse}}\textup{)}:
the FM-formality spectral sequence collapses the tower of
configuration spaces $\overline{C}_{p+2}(X)$ to the
curve-level $\mathcal{D}_X$-Ext via bar-concentration, so the
geometric shift~$[p+2]$ on $\overline{C}_{p+2}(X)$ is cancelled
by the totalization shift~$[-p]$ and only the base-curve
shift~$[2]$ survives.
The $\omega_X$ twist encodes the dualizing sheaf.
\end{theorem}

\begin{proof}
Lemma~\ref{lem:chirhoch-descent} identifies the derived chiral
Hochschild complexes with the $\Sigma$-coinvariant descents of the
homotopy Koszul dual factorization algebras:
\[
RHH_{\mathrm{ch}}(\cA)
\simeq
\bigl((\cA)^!_\infty\bigr)_{\Sigma},
\qquad
RHH_{\mathrm{ch}}(\cA^!)
\simeq
\bigl((\cA^!)^!_\infty\bigr)_{\Sigma}.
\]
The same lemma records the corrected comparison chain
\[
\bar{B}^{\mathrm{ch}}(\cA)
\longrightarrow
\cA^i:=H^*\bigl(\bar{B}^{\mathrm{ch}}(\cA)\bigr)
\xrightarrow{\ \mathbb{D}_X\ }
\cA^!,
\]
and likewise with $\cA$ and $\cA^!$ interchanged.
Thus the bar coalgebra, the dual coalgebra, and the Koszul dual
algebra stay separated throughout the argument.

Apply Lemma~\ref{lem:hochschild-shift-computation} to the filtered
complexes $RHH_{\mathrm{ch}}(\cA)$ and $RHH_{\mathrm{ch}}(\cA^!)$.
At each bar degree~$p$, the corresponding $E_2$-terms are the
curve-level Ext groups of the degree-$p$ pieces of the two Koszul
dual algebras.
By the corrected comparison chains
\[
\bar{B}^{\mathrm{ch}}(\cA)\to \cA^i \xrightarrow{\mathbb{D}_X}\cA^!,
\qquad
\bar{B}^{\mathrm{ch}}(\cA^!)\to (\cA^!)^i \xrightarrow{\mathbb{D}_X}\cA,
\]
the coefficient systems on the two $E_2$-pages are exchanged by
curve-level Verdier duality.
Curve-level Verdier duality therefore gives, bar degree by bar degree,
\[
E_2^{r,p}(\cA)
\;\cong\;
\bigl(E_2^{2-r,p}(\cA^!)\bigr)^\vee \otimes \omega_X.
\]
Because the collision-depth spectral sequences of
Lemma~\ref{lem:hochschild-shift-computation} degenerate at~$E_2$,
the same duality passes to the abutments.
The uniform shift is exactly the shift~$[2]$ computed there, so
\[
RHH_{\mathrm{ch}}(\cA)
\;\simeq\;
R\mathrm{Hom}\bigl(RHH_{\mathrm{ch}}(\cA^!),\,\omega_X[2]\bigr),
\]
which is~\eqref{eq:hochschild-H-derived}. Taking cohomology gives
\[
\ChirHoch^n(\cA)
\;\cong\;
\ChirHoch^{2-n}(\cA^!)^\vee \otimes \omega_X.
\]

The same degree reflection is visible deformation-theoretically:
the Kodaira--Spencer map
\textup{(}Theorem~\textup{\ref{thm:kodaira-spencer-chiral-complete}}\textup{)}
and the module Koszul duality equivalence
\textup{(}Theorem~\textup{\ref{thm:e1-module-koszul-duality}}\textup{)}
identify the tangent complexes on the two sides, while
Lemma~\ref{lem:hochschild-shift-computation} supplies the same
curve-level shift~$[2]$.
\end{proof}

\begin{remark}[Proof infrastructure]
The proof uses the bar-cobar quasi-isomorphism at all genera
(Theorem~\ref{thm:higher-genus-inversion}) and the Kodaira--Spencer map
for Koszul pairs
(Theorem~\ref{thm:kodaira-spencer-chiral-complete}).
\end{remark}

\begin{theorem}[Polynomial growth of chiral Hochschild cohomology
\textup{(}Theorem~H, growth clause\textup{)}; \ClaimStatusProvedHere]
\label{thm:hochschild-polynomial-growth}
\index{Hochschild cohomology!polynomial growth|textbf}
\textup{[Regime: quadratic on the Koszul locus
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

Let $\cA$ be a chiral Koszul algebra on a smooth projective curve~$X$,
and let $\cA^!$ denote its Koszul dual. Then:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Concentration \textup{(}cohomological amplitude, not
 virtual dimension\textup{)}.}\;
 $\ChirHoch^n(\cA) = 0$ for $n < 0$ and $n > 2$.
 The nonvanishing range is $0 \leq n \leq 2$.

\item \emph{Polynomial growth.}\;
 The Hochschild--Hilbert series
 \[
 P_{\cA}(t)
 \;:=\;
 \sum_{n \geq 0} \dim \ChirHoch^n(\cA)\,t^n
 \]
 is a polynomial of degree at most~$2$. More precisely,
 \begin{equation}\label{eq:hoch-hilbert-polynomial}
 P_{\cA}(t)
 \;=\;
 \dim Z(\cA)
 + \dim \ChirHoch^1(\cA)\,t
 + \dim Z(\cA^!)\,t^2,
 \end{equation}
 where $Z(\cA) = \ChirHoch^0(\cA)$ is the center and the symmetry
 $\dim \ChirHoch^0(\cA) = \dim \ChirHoch^2(\cA^!)$ comes from
 Theorem~\textup{\ref{thm:main-koszul-hoch}}.

\item \emph{Koszul functoriality.}\;
 The polynomial $P_{\cA}(t)$ is determined by the Koszul dual pair:
 \[
 P_{\cA}(t) + P_{\cA^!}(t)
 \;=\;
 (\dim Z(\cA) + \dim Z(\cA^!))(1+t^2)
 + (\dim \ChirHoch^1(\cA) + \dim \ChirHoch^1(\cA^!))\,t,
 \]
 and the palindromic duality
 $P_{\cA}(t) = t^2\,P_{\cA^!}(t^{-1})$
 holds under the same Koszul-locus hypotheses
 \textup{(}the Koszul duality
 $\ChirHoch^n(\cA) \cong \ChirHoch^{2-n}(\cA^!)^\vee \otimes \omega_X$
 from Theorem~\textup{\ref{thm:main-koszul-hoch}}
 exchanges the constant and leading coefficients).
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(a): fix a bar degree~$p$.
Lemma~\ref{lem:hochschild-shift-computation}, with the
configuration-space collapse justified by
Proposition~\ref{prop:fm-tower-collapse}, furnishes a
first-quadrant spectral sequence
\[
E_2^{r,s}(p)=0 \text{ for } s\neq p,
\qquad
E_2^{r,p}(p)\cong
\Ext_{\mathcal{D}_X}^r\!\bigl((\cA^!)_p,\omega_X\bigr),
\]
and this spectral sequence degenerates at~$E_2$.
Because $X$ is a smooth projective curve,
\[
\Ext_{\mathcal{D}_X}^r\!\bigl((\cA^!)_p,\omega_X\bigr)=0
\qquad\text{for } r\notin\{0,1,2\},
\]
so every bar-degree summand of the Hochschild total complex has
cohomological amplitude~$[0,2]$.
The totalization is again first-quadrant, hence
$\ChirHoch^n(\cA)=0$ for $n<0$, and the amplitude bound gives
$\ChirHoch^n(\cA)=0$ for $n>2$.
Thus the only possible nonzero degrees are $0$, $1$, and~$2$.

Part~(b): part~(a) implies that $P_\cA(t)$ is a polynomial of
degree at most~$2$. Its constant term is
$\dim \ChirHoch^0(\cA)=\dim Z(\cA)$. For the quadratic term,
set $n=2$ in Theorem~\ref{thm:main-koszul-hoch}:
\[
\ChirHoch^2(\cA)
\;\cong\;
\ChirHoch^0(\cA^!)^\vee \otimes \omega_X.
\]
Because $\omega_X$ is a line bundle on the fixed curve~$X$, it
does not change the dimension. Therefore
\[
\dim \ChirHoch^2(\cA)
\;=\;
\dim \ChirHoch^0(\cA^!)
\;=\;
\dim Z(\cA^!),
\]
which is exactly~\eqref{eq:hoch-hilbert-polynomial}.

Part~(c): applying Theorem~\ref{thm:main-koszul-hoch} in degrees
$n=0,1,2$ gives
\[
\dim \ChirHoch^0(\cA)=\dim \ChirHoch^2(\cA^!),
\qquad
\dim \ChirHoch^1(\cA)=\dim \ChirHoch^1(\cA^!),
\qquad
\dim \ChirHoch^2(\cA)=\dim \ChirHoch^0(\cA^!).
\]
If
\[
P_\cA(t)=a_0+a_1 t+a_2 t^2,
\qquad
P_{\cA^!}(t)=a_2+a_1 t+a_0 t^2,
\]
then
\[
t^2 P_{\cA^!}(t^{-1})
= a_0 + a_1 t + a_2 t^2
= P_\cA(t),
\]
which proves the palindromic identity. Adding the two degree-$2$
polynomials termwise gives the displayed formula for
$P_\cA(t)+P_{\cA^!}(t)$.
\end{proof}

\begin{remark}[Alternative proof via deformation theory]
There is a second route to
Theorem~\ref{thm:hochschild-polynomial-growth}\textup{(a)}
and to the polynomiality statement in
\textup{(b)} that does not use
Theorem~\ref{thm:hochschild-bar-cobar} or the
bar-collision spectral sequence. It is the chiral analogue of
Gerstenhaber's deformation-theoretic argument.

By Definition~\ref{def:cyclic-deformation-elementary}, the formal
deformation problem of~$\cA$ is governed by the cyclic deformation
object. In the tangent-complex indexing convenient for the formal
moduli problem, one reads off the infinitesimal data as
\[
Z(\cA)=\ChirHoch^0(\cA),\qquad
T_\cA=\ChirHoch^1(\cA),\qquad
\operatorname{Obs}_\cA=\ChirHoch^2(\cA).
\]
Thus $\ChirHoch^1(\cA)$ controls first-order tangent directions and
$\ChirHoch^2(\cA)$ controls obstructions. The degree-$0$ term is the
center; for the connected examples of Theorem~H this is the scalar
identity line. This is the deformation-theoretic reindexing of the
usual Gerstenhaber cochain grading.

The dimension bound is then a local-to-global statement. The chiral
deformation object is valued in holonomic $\cD_X$-modules, so on a
smooth curve the derived global-sections functor contributes at most
one cohomological step. The chiral product itself contributes one
internal deformation step because the local deformation problem is
binary. In the unshifted Hochschild grading this gives
\[
[0,1+1]=[0,2].
\]
Therefore
\[
\ChirHoch^n(\cA)=0\qquad\text{for }n\notin\{0,1,2\}.
\]
This recovers the concentration in degrees $\{0,1,2\}$ independently
of Lemma~\ref{lem:hochschild-shift-computation}.

Once one knows that the deformation problem is finite-dimensional on
the Koszul locus, only the three groups
$\ChirHoch^0(\cA)$, $\ChirHoch^1(\cA)$, and $\ChirHoch^2(\cA)$ can
contribute. Therefore
\[
P_\cA(t)=\sum_{n\ge 0}\dim \ChirHoch^n(\cA)\,t^n
\]
is automatically a polynomial of degree at most~$2$:
\[
P_\cA(t)
=
\dim Z(\cA)
+\dim \ChirHoch^1(\cA)\,t
+\dim \ChirHoch^2(\cA)\,t^2.
\]
Theorem~\ref{thm:main-koszul-hoch} then identifies the quadratic
coefficient with $\dim Z(\cA^!)$, recovering
\eqref{eq:hoch-hilbert-polynomial}. This does not remove the
Koszul-locus hypothesis: the amplitude estimate is dimension-theoretic,
but outside the finite-type or perfectness regime one still lacks the
finiteness input needed to interpret $P_\cA(t)$ as a polynomial.
\end{remark}

\begin{remark}[Geometric substrate (Volume~II)]
\label{rem:theorem-h-lagrangian}
\index{Lagrangian self-intersection!Theorem H}
Volume~II interprets this as the HKR theorem for Lagrangian
embeddings: the chiral Hochschild complex is the normal complex of
$\mathcal{L} \hookrightarrow \mathcal{M}$, and the polynomial
growth bound reflects the finite excess dimension of
$\mathfrak{S} = \mathcal{L} \times_{\mathcal{M}} \mathcal{L}$.
\end{remark}

\begin{remark}[Chiral vs classical Hochschild: structural vs dimensional]
\label{rem:critical-level-dimensional-divergence}
%: AP-CY64. Three-way Hochschild confusion.
Theorem~\ref{thm:hochschild-polynomial-growth} is a specifically
\emph{chiral} result: the concentration in degrees $\{0,1,2\}$
follows from the de~Rham amplitude bound
$[0, 2\dim_\bC X] = [0, 2]$ for $\cD_X$-module Ext on a curve.
Three invariants must be distinguished:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item $\ChirHoch^*(\cA)$: chiral Hochschild cochains.
  Concentrated in $\{0,1,2\}$ (this theorem).
  For the Heisenberg: $\dim = 3$.
\item $\HH^*(A_{\mathrm{mode}}, A_{\mathrm{mode}})$: classical
  Hochschild cochains of the mode algebra (an associative algebra
  in $\Vect$).  For the Weyl algebra:
  $\HH^0(A_1) = \bC$, $\HH^n(A_1) = 0$ for $n \ge 1$
  (total dimension~$1$).  This is \emph{more} concentrated
  than~$\ChirHoch^*$, not less.
\item $H^*_{\mathrm{cont}}(\mathrm{Lie}(\cA); \bC)$:
  Gel'fand--Fuchs continuous Lie cohomology of the
  positive-mode subalgebra
  $L_+ = \bigoplus_{n \ge 1} \bC \cdot L_n$.
  For the Virasoro: $H^*(L_+; \bC) = \bC[c_2]$
  with $|c_2| = 2$ (Goncharova; Fuks,
  \emph{Cohomology of Infinite-Dimensional Lie Algebras},
  Theorem~1.4.3): a polynomial ring, unbounded.
\end{enumerate}
At \emph{generic} level, $\ChirHoch^*(\cA)$ and
$\HH^*(A_{\mathrm{mode}})$ have the same cohomological
dimension (both finite, both concentrated).  The genuine
difference is \emph{structural}: $\ChirHoch^*$ carries an
$\Etwo$-algebra structure with spectral parameters from the
chiral endomorphism operad, while
$\HH^*(A_{\mathrm{mode}})$ carries $\Etwo$ from the Deligne
conjecture (abstract, no spectral data).

The \emph{only} regime where the two genuinely diverge in
\emph{dimension} is the \textbf{critical level} $k = -h^\vee$:
here $\ChirHoch^*$ becomes infinite-dimensional
(the Feigin--Frenkel centre
$\mathrm{Fun}(\mathrm{Op}_{\fg^\vee}(D))$ populates $\ChirHoch^0$),
while $\HH^*(A_{\mathrm{mode}})$ remains finite.
This is the scope boundary of Theorem~H: the Koszul hypothesis
fails at critical level, and the FM-tower collapse
(Proposition~\ref{prop:fm-tower-collapse}) no longer applies.
\end{remark}

\begin{corollary}[Deformation-obstruction exchange at genus \texorpdfstring{$0$}{0}; \ClaimStatusProvedHere]\label{cor:def-obs-exchange-genus0}
\index{deformation-obstruction!genus-0 exchange}
For a Koszul pair $(\mathcal{A}, \mathcal{A}^!)$ on a smooth projective curve $X$, the first-order deformations of $\mathcal{A}$ are dual to the primary obstructions of $\mathcal{A}^!$:
\begin{equation}\label{eq:def-obs-genus0}
\ChirHoch^2(\mathcal{A}) \;\cong\; \ChirHoch^0(\mathcal{A}^!)^{\vee} \otimes \omega_X.
\end{equation}
More generally, the genus-$0$ deformation complex of $\mathcal{A}$ is dual to the genus-$0$ obstruction complex of $\mathcal{A}^!$ with a shift by~$2$.
\end{corollary}

\begin{proof}
Set $n = 2$ in Theorem~\ref{thm:main-koszul-hoch}: $\ChirHoch^2(\mathcal{A}) \cong \ChirHoch^{2-2}(\mathcal{A}^!)^\vee \otimes \omega_X = \ChirHoch^0(\mathcal{A}^!)^\vee \otimes \omega_X$. Here $\ChirHoch^2(\mathcal{A})$ classifies first-order deformations of~$\mathcal{A}$, and $\ChirHoch^0(\mathcal{A}^!) = Z(\mathcal{A}^!)$ is the center of the Koszul dual. The duality exchanges the deformation space of one algebra with the center of the other, incarnating ``complementarity'' at the level of Hochschild cohomology.
\end{proof}

\begin{remark}\label{rem:def-obs-higher-genus}
At genus $g \geq 1$, the exchange is Theorem~\ref{thm:quantum-complementarity-main} (Theorem~C): $Q_g(\mathcal{A}) \oplus Q_g(\mathcal{A}^!) \cong H^*(\overline{\mathcal{M}}_g, Z(\mathcal{A}))$. The genus-$0$ corollary is the seed from which higher-genus complementarity grows via the Faber--Pandharipande mechanism (Theorem~\ref{thm:genus-universality}).
\end{remark}

\begin{example}[Heisenberg specialization]\label{ex:heisenberg-curved-specialization}
For the Heisenberg algebra $\mathcal{H}_k$, the curved $A_\infty$ structure on the Koszul dual $\mathrm{Sym}^{\mathrm{ch}}(V^*)$ has $m_0 = -k \cdot \omega$ and $m_n = 0$ for $n \geq 3$: the curvature is the entire obstruction, with no higher operations (\S\ref{sec:frame-genus1}). This is the simplest nontrivial instance of the deformation-obstruction exchange above: $\ChirHoch^2(\mathcal{H}_k) = \mathbb{C}$ (the level deformation) is dual to $\ChirHoch^0(\mathrm{Sym}^{\mathrm{ch}}(V^*))^\vee \otimes \omega_X = \mathbb{C}$ (the center of the dual).
\end{example}


%================================================================
% FORMALITY, MODULI, AND OPERADIC PERSPECTIVES ON KOSZULNESS
%================================================================

\subsection{Formality, moduli, and operadic perspectives on Koszulness}
\label{subsec:formality-moduli-operadic}

The modular
convolution algebra $\gAmod$ carries the universal Maurer--Cartan
element $\Theta_{\cA}$
(Theorem~\ref{thm:mc2-bar-intrinsic}); every structural property
of~$\cA$ is a property of~$\Theta_{\cA}$. Four
formality-type conditions on~$\gAmod$ and their consequences for
Koszulness follow.

\medskip

\begin{proposition}[$\Etwo$-formality of chiral Hochschild cohomology;
\ClaimStatusProvedHere]
\label{prop:e2-formality-hochschild}
\index{formality!$\Etwo$-chiral Hochschild}
\index{Hochschild cohomology!$\Etwo$-formality}
Let $\cA$ be a chirally Koszul algebra on a smooth projective
curve~$X$. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\ChirHoch^*(\cA)$ is formal as an $\Etwo$-algebra:
 the $\Etwo$ quasi-isomorphism type of $\ChirHoch^*(\cA)$ is
 determined by the graded algebra $H^*(\ChirHoch(\cA))$ with its
 cup product and degree-$1$ bracket.

\item All higher $\Etwo$-operations \textup{(}braces of
 degree~$\geq 3$, Massey products, $A_\infty$ corrections\textup{)}
 are cohomologically trivial.
\end{enumerate}
\end{proposition}

\begin{proof}
By Theorem~\ref{thm:hochschild-polynomial-growth},
$\ChirHoch^n(\cA) = 0$ for $n \notin \{0,1,2\}$.
The $\Etwo$-operations of degree~$k$ on $H^*(\ChirHoch(\cA))$
are maps
$H^{n_1} \otimes \cdots \otimes H^{n_k} \to H^{n_1 + \cdots + n_k - k + 1}$.
For $k \geq 3$, the source lives in total degree
$n_1 + \cdots + n_k \geq 0$ and the target in degree
$\leq n_1 + \cdots + n_k - 2$. Since each $n_i \in \{0,1,2\}$,
the target degree is at most $2k - 2$; but for the target to be
nonzero it must lie in $\{0,1,2\}$, which forces $2k - 2 \geq 0$
(automatic) and $n_1 + \cdots + n_k - k + 1 \leq 2$, i.e.\
$n_1 + \cdots + n_k \leq k + 1$. With each $n_i \geq 0$ and
$k \geq 3$ inputs, the inputs are almost all in degree~$0$.
The brace $b_{k-1}(a; a_1, \ldots, a_{k-1})$ for $a \in H^p$,
$a_i \in H^{q_i}$ has target degree $p + \sum q_i - (k-1)$.
On the bar side, the PBW collapse
(Theorem~\ref{thm:bar-concentration}) gives
$\barB^{\mathrm{ch}}(\cA)^{p,q} = 0$ for $p \neq q$,
so the braces factor through a single diagonal line in the
bar bigrading. The Kontsevich--Tamarkin formality
(Theorem~\ref{thm:e2-formality}) applied to the configuration-space
model of the $\Etwo$-structure then shows that all higher braces are
exact: the bar spectral sequence that collapses at~$E_2$ forces the
higher $\Etwo$-operations to be coboundaries.

Explicitly: obstructions to $\Etwo$-formality are Hochschild
cochains of negative \emph{excess} $e := \sum n_i - k - p$, where
$p$ is the target degree. Concentration in $\{0,1,2\}$ forces
$e \leq 2 - k$ for $k \geq 3$.
The deformation retraction from
$\barB^{\mathrm{ch}}(\cA)$ to its cohomology, which exists by
PBW collapse, provides the contracting homotopy that trivializes
these operations. The ``concentration-implies-formality''
argument (cf.\ \cite{LV12}, \S10.3) applied to the three-term
complex $H^0 \oplus H^1 \oplus H^2$ gives the result.
\end{proof}

\begin{remark}[What $\Etwo$-formality adds beyond Theorem~H]
\label{rem:e2-formality-vs-thmH}
Theorem~\ref{thm:hochschild-polynomial-growth} gives concentration.
Proposition~\ref{prop:e2-formality-hochschild} extracts a strictly
stronger consequence: the $\Etwo$-algebra structure on
$H^*(\ChirHoch(\cA))$ is determined by the cup product and the
Gerstenhaber bracket alone. The secondary Borcherds
operations $F_n$ from the homotopy chiral algebra structure on
$\barB^{\mathrm{ch}}(\cA)$
(Theorem~\ref{thm:cech-hca}, Pillar~A) are exact for
$n \geq 3$, and $\Etwo$-formality is automatic from
PBW concentration, not an additional hypothesis.

The converse ($\Etwo$-formality implies Koszulness) is false.
A non-Koszul algebra whose Hochschild cohomology happens
to concentrate in three degrees would also be $\Etwo$-formal
by the same argument. A stronger converse would require
the scalar-orbit formality problem discussed
below, for which no converse is proved here
\textup{(}Theorem~\textup{\ref{thm:convolution-formality-one-channel}}\textup{)}.
\end{remark}

\begin{theorem}[Scalar universal class implies convolution
formality along its distinguished orbit;
\ClaimStatusProvedHere]
\label{thm:convolution-formality-one-channel}
\index{formality!convolution algebra}
\index{one-channel!scalar-orbit formality problem}
\index{scalar saturation|see{one-channel}}
Let $\cA$ be a modular Koszul chiral algebra.
The modular convolution algebra
\[
\gAmod
\;=\;
\prod_{g,n}\,
\operatorname{Hom}_{\Sigma_n}\!\bigl(
 C_*(\overline{\cM}_{g,n}),\;
 \operatorname{End}_{\cA}(n)
\bigr)
\]
carries the five-component differential
$D = d_{\mathrm{int}} + [\tau,-] + d_{\mathrm{sew}}
 + d_{\mathrm{pf}} + \hbar\Delta$
and the universal Maurer--Cartan element
$\Theta_{\cA} := D_{\cA} - d_0
\in \MC(\gAmod)$
\textup{(}Theorem~\textup{\ref{thm:mc2-bar-intrinsic})}.
Assume the full universal Maurer--Cartan element is scalar:
\begin{equation}\label{eq:one-channel-formality}
\Theta_{\cA}
\;=\;
\kappa(\cA) \cdot \eta \otimes \Lambda.
\end{equation}
Then the quantum $L_\infty$-structure is formal along the
distinguished scalar Maurer--Cartan orbit of\/~$\Theta_{\cA}$:
the higher transferred brackets vanish on the one-dimensional
scalar line $\mathbb{C}\!\cdot\!\eta \otimes \Lambda$, and the MC
equation restricts there to the scalar genus identities.
No converse is proved here. In particular, one-channel
minimal-model concentration
$\Theta_{\cA}^{\min} = \eta \otimes \Gamma_{\cA}$ does
\emph{not} by itself imply the scalar identity
\eqref{eq:one-channel-formality}.
\end{theorem}

\begin{proof}
Throughout this proof we write $\kappa$ for $\kappa(\cA)$.
Suppose $\Theta_{\cA} = \kappa \cdot \eta \otimes \Lambda$.
By Theorem~\ref{thm:operadic-complexity-detailed},
one-channel forces shadow depth $r_{\max}(\cA) = 2$,
hence $A_\infty$-depth $d_\infty(\cA) = 2$ and
$L_\infty$-formality level $f_\infty(\cA) = 2$.
The genus-$0$ transferred $L_\infty$ brackets therefore
satisfy $\ell_k^{(0),\mathrm{tr}} = 0$ for $k \geq 3$:
the genus-$0$ convolution algebra is formal.

For the full scalar orbit, the shadow
obstruction tower terminates at degree~$2$:
$\Theta_{\cA}^{(\le r)} = \kappa \cdot \eta \otimes \Lambda$
for all~$r$. The obstruction classes
$o^{(r+1)}(\cA) \in H^2(F^{r+1}\gAmod / F^{r+2}\gAmod, d_2)$
vanish for all $r \geq 2$
(Theorem~\ref{thm:nms-all-degree-master-equation}).
Since the genus-$g$ quantum brackets $\ell_k^{(g)}$ for
$g \geq 1$ are induced by sewing on $\overline{\cM}_{g,n}$,
and sewing applied to the scalar element
$\kappa \cdot \eta \otimes \Lambda$ produces the scalar
genus-$g$ curvature $\kappa^g \cdot \eta_g \otimes \Lambda_g$
(which lies in the image of the differential, not in
independent cohomology), the transferred higher-genus brackets
$\ell_k^{(g),\mathrm{tr}}$ also vanish for $k \geq 3$.
This gives formality of the distinguished scalar orbit of
$\Theta_{\cA}$ inside~$\gAmod$.
\end{proof}

\begin{remark}[Scalar-orbit formality and scalar saturation]
\label{rem:convolution-formality-cg}
\index{Chriss--Ginzburg principle!convolution formality}
\emph{Forward direction} (writing $\kappa$ for $\kappa(\cA)$).\;
If $\Theta_{\cA} = \kappa \cdot \eta \otimes \Lambda$, the
MC equation $D \Theta + \tfrac{1}{2}[\Theta, \Theta] = 0$
reduces to a scalar identity at each $(g,n)$:
$[\eta \otimes \Lambda, \eta \otimes \Lambda]$ factors through the
metric contraction, so the higher $L_\infty$-brackets $\ell_k$
($k \geq 3$) act trivially on
$\bC \cdot \eta \otimes \Lambda$. Hence
$\gAmod$ is formal along the orbit of~$\Theta_{\cA}$.

\emph{Converse / open direction.}\;
Current methods do \emph{not} show that formality of the full
quantum $L_\infty$-algebra forces scalar saturation, nor that
one-channelity alone implies formality. The strongest proved
input is the one-channel minimal-model statement
$\Theta_{\cA}^{\min}=\eta\otimes\Gamma_{\cA}$
\textup{(}Corollary~\textup{\ref{cor:scalar-saturation}}\textup{)};
identifying $\Gamma_{\cA}$ with
$\kappa(\cA)\Lambda$ is the open tautological-purity step outside
the proved scalar lane.

\emph{Relation to the shadow obstruction tower.}\;
The non-scalar universal classes
of~\S\ref{subsec:non-scalar-theta} measure the deviation of
$\Theta_{\cA}$ from the scalar line. The cubic shadow~$C$, quartic resonance class~$Q$,
and all higher shadows $\mathrm{Sh}_r$ are the
\emph{obstructions to formality}: the higher-order
corrections preventing $\Theta_{\cA}$ from lying on the
scalar line.

\emph{Pillar~C interaction} (Mok~\cite{Mok25}):
the planted-forest coefficient algebra $G_{\mathrm{pf}}$
(Definition~\ref{def:planted-forest-coefficient-algebra}) controls
the non-formal corrections. Vanishing planted-forest
contributions removes one source of deviation from the scalar
orbit, but no converse criterion for full convolution formality
is proved here
(Remark~\ref{rem:full-homotopy-why}).
\end{remark}

\begin{remark}[Hierarchy: Koszulness, modular Koszulness, formality]
\label{rem:formality-vs-koszul}
Three properties of increasing strength:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Koszulness} (genus~$0$): the bar spectral sequence
 collapses at~$E_2$
 (Theorem~\ref{thm:bar-concentration}).

\item \emph{Modular Koszulness} (all genera): MK3 extends PBW
 collapse; the scalar trace $\kappa(\cA)$ is the sole survivor
 in the modular bar cohomology at $g \geq 1$.

\item \emph{Scalar-orbit convolution formality} (structural, on the
 proved scalar lane): when the full universal class is scalar,
 the quantum $L_\infty$-structure is formal along its
 distinguished scalar orbit, by
 Theorem~\ref{thm:convolution-formality-one-channel}.
\end{enumerate}
On the proved scalar lane, the implication
$\text{(c)} \Rightarrow \text{(b)} \Rightarrow \text{(a)}$
holds. Outside that lane, the first converse-type problem is
exactly the non-scalar shadow obstruction tower
(\S\ref{subsec:non-scalar-theta}); the second is the
higher-genus curvature.
\end{remark}

\begin{conjecture}[MC moduli smoothness at the Koszul locus;
\ClaimStatusConjectured]
\label{conj:mc-moduli-smoothness}
\index{Maurer--Cartan!moduli smoothness}
Let $\cA$ be a chiral algebra on a smooth projective curve~$X$
with universal MC element $\Theta_{\cA} \in \MC(\gAmod)$
\textup{(}Theorem~\textup{\ref{thm:mc2-bar-intrinsic})}.
Then $\cA$ is chirally Koszul if and only if
\begin{equation}\label{eq:mc-smoothness}
H^2\!\bigl(\gAmod,\,
 \operatorname{ad}(\Theta_{\cA})\bigr)
\;=\; 0,
\end{equation}
i.e.\ the MC moduli stack $\MC(\gAmod)$ is smooth
at~$\Theta_{\cA}$.
\end{conjecture}

\begin{remark}[Identifying the obstruction space]
\label{rem:mc-smoothness-pbw}
The twisted cohomology
$H^2(\gAmod, \operatorname{ad}(\Theta_{\cA}))$ admits a direct
identification.
At genus~$0$, the $(g,n) = (0,3)$ component of the
$\operatorname{ad}(\Theta_{\cA})$-twisted complex is
$\ChirHoch^2(\cA)$
(Corollary~\ref{cor:def-obs-exchange-genus0}), and for a
Koszul algebra this equals
$Z(\cA^!)^\vee \otimes \omega_X$: a finite-dimensional space
completely controlled by the Koszul dual.

At genus~$g \geq 1$, the contributions come from the modular bar
complex. The modular Koszulness axiom MK3 forces the bar spectral
sequence to collapse at~$E_1$ in all bidegrees, which kills the
higher-genus components of
$H^2(\gAmod, \operatorname{ad}(\Theta_{\cA}))$.
The shadow obstruction tower
(Corollary~\ref{cor:shadow-extraction}) then determines
$\Theta_{\cA}$ from~$\kappa(\cA)$, leaving no room for obstructed
deformations.

The forward direction, that Koszulness implies
vanishing~\eqref{eq:mc-smoothness}, therefore follows from the
PBW collapse at all genera. The converse, that smoothness implies
Koszulness, is the nontrivial content: it asserts that obstructions
to the bar spectral sequence collapsing are \emph{exactly} detected
by twisted $H^2$. A proof would require showing that every
non-collapsing class in the bar complex produces a nontrivial
element of $H^2(\gAmod, \operatorname{ad}(\Theta_{\cA}))$.
For the Heisenberg algebra, both sides are one-dimensional:
$H^2 = \bC$ classifies the level deformation, and the obstruction
is the curvature $m_0 = -k \cdot \omega$
(Example~\ref{ex:heisenberg-curved-specialization}).
\end{remark}

\begin{theorem}[Bifunctor obstruction decomposition;
\ClaimStatusProvedHere]
\label{thm:bifunctor-obstruction-decomposition}%
\index{bifunctor obstruction!decomposition}
\index{Robert-Nicoud--Wierstra!no-bifunctor obstruction}
The convolution $sL_\infty$-algebra
$\operatorname{hom}_\alpha(\barB^{\mathrm{ch}}(\cA),\, \cA)$
is functorial in each slot separately but fails as a bifunctor
\textup{(\cite{RNW19}, Theorem~6.6;
Remark~\textup{\ref{rem:two-level-convention})}}.
For a chirally Koszul algebra~$\cA$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The degree-$3$ obstruction class
\[
\mathrm{obs}_3
\;\in\;
H^2\!\bigl(
 \operatorname{hom}_\alpha^{(3)}
 (\barB^{\mathrm{ch}}(\cA),\, \cA)
\bigr)
\]
is nonzero in general, but is immaterial for the MC3 categorical
lift: Koszulness makes one-slot factorization sufficient.

\item Every two-sided $\infty$-morphism that fails to exist as a
 bifunctor morphism decomposes as a one-sided coalgebra morphism
 followed by a one-sided algebra morphism, with the composition
 independent of ordering up to homotopy.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(i): the obstruction class $\mathrm{obs}_3$ is the failure of
$\operatorname{hom}_\alpha$ to extend to $\infty$-morphisms in both
slots simultaneously (\cite{RNW19}, Theorem~6.6). For chirally
Koszul~$\cA$, the bar-cobar counit
$\Omega(\barB(\cA)) \xrightarrow{\sim} \cA$ is a quasi-isomorphism;
the one-slot convention
(Remark~\ref{rem:two-level-convention}) fixes the cooperad slot and
varies the algebra by $\infty$-morphisms. The bar-cobar inversion
gives a canonical strict model, so both-slot variation is
unnecessary: the MC3 categorical lift proceeds one slot at a time
(Theorem~\ref{thm:mc3-type-a-resolution}).

Part~(ii): a two-sided $\infty$-morphism $(f, g)$ with $f$ on the
coalgebra side and $g$ on the algebra side satisfies
$\partial f + f \star g = 0$; by the one-slot convention, this
factors as $f$~followed by~$g$ with the composition determined up
to homotopy by the contractibility of the space of
$\infty$-morphisms between quasi-isomorphic objects.
\end{proof}

\begin{remark}[Heisenberg test case and the MC3 frontier]
\label{rem:bifunctor-analysis}
\emph{Testability.}\;
For the Heisenberg algebra $\cH_k$, the obstruction
$\mathrm{obs}_3$ lives in the two-dimensional space
$H^2(\operatorname{hom}_\alpha^{(3)}
 (\barB^{\mathrm{ch}}(\cH_k), \cH_k))$.
An explicit computation: $\barB^{\mathrm{ch}}(\cH_k)$ is
concentrated in bar degree~$1$
(Theorem~\ref{thm:bar-concentration}),
so $\operatorname{hom}_\alpha^{(3)}$ reduces to maps from
the triple self-product of the cogenerators. The obstruction is
the failure of the Leibniz rule for the simultaneous
coalgebra-algebra functoriality, which is nonzero even for this
simplest example because the Koszul duality functor itself is
not strict-monoidal.

\emph{Structural origin.}\;
The no-bifunctor theorem of~\cite{RNW19} (\S6) is universal:
$\mathrm{obs}_3 \neq 0$ for \emph{any} cooperad-operad pair.
The content of part~(ii) is that Koszulness provides a
\emph{one-slot workaround}: the Quillen equivalence
$\barB_\kappa \dashv \Omega_\kappa$
(Theorem~\ref{thm:quillen-equivalence-chiral})
transports $\infty$-morphisms through one slot at a time.
This is why the MC3 resolution
(Theorem~\ref{thm:categorical-cg-all-types}, Corollary~\ref{cor:mc3-all-types}) succeeds: each step
on the proved all-types surface
\textup{(}categorical prefundamental Clebsch--Gordan via
multiplicity-free $\ell$-weights together with the generated-core DK
comparison\textup{)} is a one-slot operation. The later chromatic,
completion, and compact-extension steps belong to the separate
post-CG packet, reduced in type~$A$ but not proved in all types.
The all-types generalization therefore proceeds one slot at a time on
the evaluation-generated core; the decomposition property of
part~(ii) explains why this is sufficient on that proved surface.
\end{remark}

\begin{remark}[Operadic inheritance of Koszulness]
\label{rem:operadic-inheritance}
\index{Koszulness!operadic inheritance}
Chiral Koszulness should descend from Koszulness of the chiral
operad $P^{\mathrm{ch}}$ itself, just as $\Eone$-chiral Koszul
duality (Theorem~\ref{thm:e1-chiral-koszul-duality}) derives from
Koszulness of $\mathsf{Ass}$ via
Lemma~\ref{lem:operadic-koszul-transfer}.
This requires formality of $\overline{\mathrm{FM}}_n(X)$ as
operadic objects on curves; see
Theorem~\ref{thm:operadic-complexity} for the detailed
statement and verification table.
\end{remark}

\section{Example: boson-fermion duality}

\subsection{The free boson chiral algebra}

The free boson $\mathcal{B} = \mathcal{H}_k$ at level~$k$ on a curve $X$ is defined as follows:

\emph{As a chiral algebra.}
The free boson $\mathcal{B}$ is the chiral envelope of the Heisenberg Lie$^*$ algebra
$\omega_X$ (with Lie$^*$ bracket given by the residue pairing). Its vacuum module is
$\mathrm{Sym}(\omega_X \otimes t^{-1}\mathbb{C}[t^{-1}])$, a polynomial algebra on
infinitely many generators $\alpha_{-n}$ ($n \geq 1$).

\emph{Generator.} The field $\alpha(z)$ generates $\mathcal{B}$ with conformal weight $h = 1$.

\emph{Chiral multiplication.} Determined by the OPE
\[
\alpha(z_1) \alpha(z_2) = \frac{k}{(z_1-z_2)^2} + \text{regular}
\]

In terms of modes $\alpha(z) = \sum_{n \in \mathbb{Z}} \alpha_n z^{-n-1}$:
\[
[\alpha_m, \alpha_n] = k \cdot m \delta_{m+n,0}
\]
The central charge is $c = 1$ (at level $k = 1$; in general $c = 1$ for any~$k$, since the Heisenberg algebra has $c = 1$ independent of level).

\emph{Vacuum representation.} The Fock space
\[
\mathcal{F}_{\mathcal{B}} = \mathbb{C}[\alpha_{-1}, \alpha_{-2}, \ldots] |0\rangle
\]
with $\alpha_n |0\rangle = 0$ for $n \geq 0$.

\subsection{The free fermion chiral algebra}

The free fermion $\mathcal{F}$ has:

\emph{Generators.} Two fermionic fields $\psi(z), \psi^*(z)$ with $h = 1/2$.

\emph{Relations.} The OPEs
\begin{align}
\psi(z_1)\psi^*(z_2) &= \frac{1}{z_1-z_2} + \text{regular} \\
\psi(z_1)\psi(z_2) &= 0 + \text{regular} \\
\psi^*(z_1)\psi^*(z_2) &= 0 + \text{regular}
\end{align}

In modes (half-integer for Neveu--Schwarz sector):
\begin{align}
\{\psi_r, \psi^*_s\} &= \delta_{r+s,0} \\
\{\psi_r, \psi_s\} &= 0 \\
\{\psi^*_r, \psi^*_s\} &= 0
\end{align}

\emph{Fock space.}
\[
\mathcal{F}_{\mathcal{F}} = \Lambda^{\bullet}(\psi_{-1/2}, \psi_{-3/2}, \ldots, \psi^*_{-1/2}, \psi^*_{-3/2}, \ldots) |0\rangle
\]

\subsection{Establishing Koszul duality}

\begin{theorem}[Boson-fermion correspondence via lattice VOA; \ClaimStatusProvedElsewhere{} \cite{FK80}]\label{thm:boson-fermion-lattice}
The free boson $\mathcal{B}$ and free fermion $\mathcal{F}$ are related by bosonization through the rank-1 lattice vertex algebra $V_{\mathbb{Z}}$:
\[
V_{\mathbb{Z}} \supset \mathcal{B}, \qquad \mathcal{F} \cong V_{\mathbb{Z}} \quad \text{(as super vertex algebras)}
\]
\end{theorem}

\begin{remark}
This is \emph{not} Koszul duality in the operadic sense (Remark~\ref{rem:bosonization-not-koszul}). Koszul duality preserves the dimension of the generating space: if $\mathcal{A}$ has generators in a space $V$, then $\mathcal{A}^!$ has generators in $V^*$, so $\dim V = \dim V^*$. Here $\mathcal{B}$ has one generator ($\alpha$) while $\mathcal{F}$ has two generators ($\psi, \psi^*$). The Heisenberg algebra is \emph{not} Koszul self-dual: $\mathcal{H}_\kappa^! \simeq \mathrm{Sym}^{ch}(V^*)$, a commutative chiral algebra (Part~\ref{part:characteristic-datum}, the characteristic datum). The boson-fermion correspondence is instead a lattice VOA extension: the vertex operators $\psi = {:}e^{i\phi}{:}$ and $\psi^* = {:}e^{-i\phi}{:}$ lie in $V_{\mathbb{Z}}$, not in the Heisenberg subalgebra.
\end{remark}

\begin{proof}
We verify this at three levels:

\emph{Level 1: The Lattice Extension}

The free boson $\mathcal{B}$ is generated by $\alpha(z) = i\partial\phi(z)$ with OPE $\alpha(z)\alpha(w) \sim k/(z-w)^2$. The rank-1 lattice VOA $V_{\mathbb{Z}}$ extends $\mathcal{B}$ by adjoining vertex operators $e^{in\phi}$ for $n \in \mathbb{Z}$:
\[
V_{\mathbb{Z}} = \bigoplus_{n \in \mathbb{Z}} \mathcal{F}_n, \qquad \mathcal{F}_n = \mathcal{B} \cdot {:}e^{in\phi}{:}
\]
The charge-$(\pm 1)$ sectors produce the fermionic fields $\psi = {:}e^{i\phi}{:}$ and $\psi^* = {:}e^{-i\phi}{:}$.

\emph{Level 2: Bosonization}

The explicit isomorphism is given by bosonization:
\begin{align}
\psi(z) &= :e^{i\phi(z)}: \\
\psi^*(z) &= :e^{-i\phi(z)}: \\
\alpha(z) &= i\partial\phi(z)
\end{align}

where $\phi$ is the bosonic field with $\phi(z)\phi(w) \sim -\log(z-w)$.

This realizes the isomorphism at the level of vertex operators:
\[
Y_{\mathcal{F}}(\psi, z) = :e^{i\int^z \alpha}: \quad \text{(fermion as exponential of boson)}
\]

\emph{Level 3: Bar Complex of the Heisenberg}

The bar complex of $\mathcal{B}$ has underlying space:
\[
\overline{B}^{\text{ch}}(\mathcal{B}) = \text{span}\{[\alpha^{n_1}]|[\alpha^{n_2}]|\cdots|[\alpha^{n_k}]\}
\]

with coproduct:
\[
\Delta([\alpha^n]) = \sum_{i+j=n} [\alpha^i] \otimes [\alpha^j]
\]

This is the divided power coalgebra $\Gamma(V^*)$, which is the Koszul dual \emph{coalgebra}. Its linear dual is the symmetric algebra $\mathrm{Sym}(V)$, and the Koszul dual \emph{algebra} is $\mathcal{H}_\kappa^! \simeq \mathrm{Sym}^{\mathrm{ch}}(V^*)$ (Part~\ref{part:characteristic-datum}, the characteristic datum), confirming that the Heisenberg algebra is Koszul (Theorem~\ref{thm:km-chiral-koszul}) but \emph{not} Koszul self-dual. (The cobar $\Omega(\bar{B}(\mathcal{H}_\kappa))$ recovers $\mathcal{H}_\kappa$ itself.)
\end{proof}

\subsection{Computing chiral Hochschild cohomology}

\begin{computation}[Boson chiral Hochschild cohomology; \ClaimStatusProvedHere]
\label{comp:boson-hochschild}

\emph{Degree 0.}
\[
\ChirHoch^0(\mathcal{B}) = Z(\mathcal{B})
\]
the center of $\mathcal{B}$, consisting of elements whose OPE with every field is regular.
An element $a \in \mathcal{B}$ lies in the center if and only if $a(z)\alpha(w) \sim 0$ (no singular terms). Since $\alpha(z)\alpha(w) \sim k(z-w)^{-2}$, the only such elements are scalars. Thus $\ChirHoch^0 = \mathbb{C}$.

\emph{Degree 1.}
A chiral derivation $D: \mathcal{B} \to \mathcal{B}$ must satisfy the Leibniz rule for the $\lambda$-bracket: $D(\{\alpha_\lambda \alpha\}) = \{D(\alpha)_\lambda \alpha\} + \{\alpha_\lambda D(\alpha)\}$.
Since $\{\alpha_\lambda \alpha\} = \kappa\lambda$ is a scalar, the left side is $0$, and the constraint is $\{D(\alpha)_\lambda \alpha\} + \{\alpha_\lambda D(\alpha)\} = 0$.
The derivation $D(\alpha) = c \cdot \mathbf{1}$ (a scalar) satisfies this because $\{c_\lambda \alpha\} = 0$ and $\{\alpha_\lambda c\} = 0$.
This derivation is \emph{not inner}: an inner derivation by a field $a$ acts as $a_{(0)}\alpha$, but for the Heisenberg algebra $\alpha_{(0)}\alpha = 0$ (the zero mode is central: $[\alpha_0, \alpha_n] = 0$ for all $n$), and $\mathbf{1}_{(0)}\alpha = 0$. No element $a \in \mathcal{B}$ satisfies $a_{(0)}\alpha = \mathbf{1}$.
Thus $\ChirHoch^1 = \mathbb{C}$, generated by the outer derivation $D(\alpha) = \mathbf{1}$.
% CORRECTION (2026-03-28): Previously stated ChirHoch^1 = 0, conflating
% classical Whitehead (all derivations of the Weyl algebra are inner)
% with chiral Hochschild (the zero-mode alpha_{(0)} is central, so
% D(alpha) = 1 is a non-inner chiral derivation). See.

\emph{Degree 2.}
A 2-cocycle $\phi \in C^2$ defines a deformation:
\[
\alpha(z) \cdot_t \alpha(w) = \alpha(z)\alpha(w) + t\phi(z,w)
\]
The cocycle condition ensures associativity to first order. The space of such cocycles
is one-dimensional, spanned by the level deformation $\alpha(z) \alpha(w) \sim k/(z-w)^2 \mapsto (k + \epsilon t)/(z-w)^2$. Thus $\ChirHoch^2 = \mathbb{C}$.
\end{computation}

\begin{computation}[Fermion chiral Hochschild cohomology; \ClaimStatusProvedHere]
\label{comp:fermion-hochschild}

The fermion case differs from the boson in one key respect: the OPE $\psi(z)\psi^*(w) \sim 1/(z-w)$ produces a simple pole (not a double pole), so the bar differential acts on degree-$1$ generators by residue extraction rather than by the second-order Casimir. The Hochschild computation then parallels the bosonic case with the quadratic Casimir $\kappa/(z-w)^2$ replaced by the identity pairing $1/(z-w)$.

\emph{Degree~$0$.} The center $Z(\mathcal{F})$ consists of elements with regular OPE against both $\psi$ and $\psi^*$. Since $\psi(z)\psi^*(w) \sim (z-w)^{-1}$, only scalars commute with all generators, giving $\ChirHoch^0 = \mathbb{C}$.

\emph{Degree~$1$.} All derivations of the Clifford algebra are inner \cite[Ch.~9]{Weibel94}, so $\ChirHoch^1 = 0$.

\emph{Degree~$2$.} The unique deformation is the level shift $\psi(z)\psi^*(w) \sim (1+\epsilon t)/(z-w)$, giving $\ChirHoch^2 = \mathbb{C}$.
\begin{align}
\ChirHoch^0(\mathcal{F}) &= \mathbb{C} \quad \text{(scalars only)} \\
\ChirHoch^1(\mathcal{F}) &= 0 \quad \text{(rigid)} \\
\ChirHoch^2(\mathcal{F}) &= \mathbb{C} \quad \text{(level deformation)}
\end{align}
The fermion Hochschild groups differ from the boson groups at degree~$1$: $\ChirHoch^1(\mathcal{F}) = 0$ (all chiral derivations are inner) while $\ChirHoch^1(\mathcal{B}) = \mathbb{C}$ (Computation~\ref{comp:boson-hochschild}). The two algebras are \emph{not} Koszul dual (see Remark below).
\end{computation}

\begin{remark}[Boson-fermion chiral Hochschild comparison: pole order controls innerness]
\label{rem:boson-fermion-hochschild-comparison}
The boson and fermion have \emph{non-isomorphic} chiral Hochschild cohomology:
\[
\ChirHoch^n(\mathcal{B}) = (\mathbb{C}, \mathbb{C}, \mathbb{C}), \qquad
\ChirHoch^n(\mathcal{F}) = (\mathbb{C}, 0, \mathbb{C}).
\]
The discrepancy at degree~$1$ reflects the \emph{pole order} of the OPE. For the fermion, $\psi(z)\psi^*(w) \sim (z-w)^{-1}$ has a simple pole, so $\psi_{(0)}\psi^* = 1$ is nontrivial; inner derivations span all of $\mathrm{Der}(\mathcal{F})$. For the boson, $\alpha(z)\alpha(w) \sim k(z-w)^{-2}$ has no simple pole, so $\alpha_{(0)}\alpha = 0$; the outer derivation $D(\alpha) = \mathbf{1}$ survives. In general:
\begin{center}
\emph{Simple pole in the OPE $\Longrightarrow$ nontrivial zero mode $\Longrightarrow$ inner derivation.}\\
\emph{No simple pole $\Longrightarrow$ central zero mode $\Longrightarrow$ outer derivation survives.}
\end{center}
The boson and fermion are \emph{not} Koszul dual: the Heisenberg has one generator
while the fermion has two, and the bosonization correspondence is an \emph{isomorphism} via lattice VOA extension, not a Koszul duality. The Koszul dual of $\mathcal{H}_k$ is $\mathrm{Sym}^{\mathrm{ch}}(V^*)$ with curvature $m_0 = -k\omega$ (equivalently, $\mathrm{CE}(\mathfrak{h}_{-k})$ since $\mathfrak{h}$ is abelian), not $\mathcal{F}$.
\end{remark}

\subsection{The cyclic deformation complex}
\label{subsec:cyclic-deformation}

\begin{definition}[Cyclic deformation complex: elementary models]
\label{def:cyclic-deformation-elementary}
\index{cyclic deformation complex|textbf}
\index{Def cyc@$\operatorname{Def}_{\mathrm{cyc}}$|textbf}
Let $\cA$ be a chiral algebra on~$X$. The homotopy-invariant
\emph{cyclic deformation object} of~$\cA$ is a complete filtered cyclic
$L_\infty$-algebra controlling cyclic deformations of~$\cA$.
A strict presentation is the
\emph{cyclic deformation complex} $\Defcyc(\cA)$
used for calculations below.

\smallskip\noindent
\textbf{Abstract definition (H-level).}
$\operatorname{Def}_{\mathrm{cyc}}(\cA)$ is the Lie algebra object in
the $\infty$-category of cochain complexes whose Maurer--Cartan
elements parametrize flat cyclic deformations of~$\cA$ over
Artinian bases. For the full construction, which requires a cyclic
$L_\infty$ algebra over the modular operad, see
Theorem~\ref{thm:universal-MC}.

\smallskip\noindent
\textbf{Concrete models (M-level).}
For the examples treated in this monograph, explicit models are:

\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Bar coderivations.}
 $\operatorname{Def}_{\mathrm{cyc}}(\cA)_{\mathrm{bar}}
 := \operatorname{CoDer}^{\mathrm{cyc}}(\bar{B}_X(\cA))$,
 the complex of cyclic coderivations of the bar construction.
 Its Maurer--Cartan elements are exactly the curved deformations
 of the bar differential.
\item \emph{Cyclic chiral Hochschild complex.}
 $\operatorname{Def}_{\mathrm{cyc}}(\cA)_{\mathrm{Hoch}}
 := CC^*_{\mathrm{ch}}(\cA)^{\mathrm{cyc}}$,
 the cyclic-invariant part of the chiral Hochschild cochain complex
 (the complex controlling $S^1$-equivariant deformations).
\item \emph{Stable-graph operations.}
 For $\cA$ modular Koszul
 (Definition~\ref{def:modular-koszul-chiral}), the genus-$g$
 deformations are generated by stable-graph operations
 $\gamma \in \Gamma_{g,n}$, and the Maurer--Cartan equation
 splits into genus-graded components whose leading term is the
 curvature $\mcurv{g} = \kappa(\cA) \cdot \lambda_g$
 \textup{(UNIFORM-WEIGHT)}.
\end{enumerate}

The Heisenberg specialization (Chapter~\ref{ch:heisenberg-frame})
is computed via model~(a): the cyclic coderivation complex is
one-dimensional at genus~$1$, generated by the Eisenstein element
$\kappa \cdot E_2(\tau)$.
\end{definition}

\begin{remark}[Quantum \texorpdfstring{$L_\infty$}{L-infinity} versus cyclic \texorpdfstring{$L_\infty$}{L-infinity}]
\label{rem:quantum-vs-cyclic-linf}
\index{quantum L-infinity algebra@quantum $L_\infty$ algebra|textbf}
\index{loop homotopy algebra|see{quantum $L_\infty$ algebra}}
Three levels arise as the genus filtration opens:
(i)~\emph{cyclic $L_\infty$} ($g = 0$, tree-level operations);
(ii)~\emph{quantum $L_\infty$} (all $g$; Braun--Lazarev~\cite{BL15},
Markl~\cite{Markl06}: operations $m^{(g)}_n$ on stable graphs
satisfying the QME $\sum_g \hbar^g m^{(g)} = 0$);
(iii)~\emph{modular homotopy type} (coupled to factorization on
$\operatorname{Ran}(X)$,
Definition~\ref{def:modular-homotopy-theory-intro}).
The lift (i)$\to$(ii) is obstructed by $\Delta(m_0)$ (unimodularity);
Koszul chiral algebras carry full modular homotopy types via
$\Theta_\cA$ (Theorem~\ref{thm:universal-MC}).
\end{remark}

\begin{proposition}[Genus-\texorpdfstring{$0$}{0} cyclic coderivation complex;
\ClaimStatusProvedHere]\label{prop:genus0-cyclic-coderivation}
\index{cyclic deformation complex!genus-$0$ construction}
Let $\cA$ be a Koszul chiral algebra with non-degenerate
invariant bilinear form
$\langle{-},{-}\rangle_{\cA}\colon \cA\otimes\cA\to\omega_X$.
Let $\bar{B}_X(\cA) = T^c(s^{-1}\bar{\cA})$ be the reduced bar
coalgebra
\textup{(}\S\textup{\ref{sec:bar-cobar}}\textup{)}.
Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Cyclic coalgebra structure.}
 The form $\langle{-},{-}\rangle_{\cA}$ induces a non-degenerate
 cyclic pairing $\eta$ on $T^c(s^{-1}\bar{\cA})$ via
 \begin{equation}\label{eq:cyclic-coalgebra-pairing}
 \eta\bigl(s^{-1}a_1\,|\cdots|\,s^{-1}a_n,\;
 s^{-1}b_1\,|\cdots|\,s^{-1}b_n\bigr)
 \;=\;
 \sum_{j=0}^{n-1}\varepsilon_j\,
 \prod_{i=1}^{n}
 \langle a_{j+i},\,b_i\rangle_{\cA},
 \end{equation}
 where indices are cyclic modulo~$n$ and $\varepsilon_j$ is
 the Koszul sign of the cyclic permutation by~$j$ steps.

\item \emph{Cyclic coderivation sub-Lie-algebra.}
 The space
 $\operatorname{CoDer}^{\mathrm{cyc}}(\bar{B}_X(\cA))
 := \{f\in\operatorname{CoDer}(\bar{B}_X(\cA))\;:\;
 \eta(f(x),y)+(-1)^{|f||x|}\eta(x,f(y))=0\;\forall\,x,y\}$
 is a sub-Lie-algebra of
 $\operatorname{CoDer}(\bar{B}_X(\cA))$.

\item \emph{Bar differential is cyclic.}
 The bar differential $d_{\barB}\in
 \operatorname{CoDer}(\bar{B}_X(\cA))$ lies in
 $\operatorname{CoDer}^{\mathrm{cyc}}(\bar{B}_X(\cA))$.

\item \emph{Cyclic dg Lie algebra.}
 The degree-shifted complex
 $\operatorname{CoDer}^{\mathrm{cyc}}(\bar{B}_X(\cA))[1]$
 is a cyclic dg Lie algebra: the bracket $l_2 = [-,-]$
 is $\eta$-invariant and $l_1 = [d_{\barB},-]$ is
 $\eta$-skew. The Maurer--Cartan locus inherits a
 $(-1)$-shifted symplectic structure.
\end{enumerate}
\end{proposition}

\begin{proof}
(i)\enspace
The cyclic pairing~\eqref{eq:cyclic-coalgebra-pairing} is the
standard construction for cyclic coalgebras:
each bar-length-$n$ component of~$\eta$ is obtained by cyclically
summing the tensor product of~$\langle{-},{-}\rangle_{\cA}$ over
the $n$~factors. Non-degeneracy of~$\eta$ on each bar-length
component follows from non-degeneracy
of~$\langle{-},{-}\rangle_{\cA}$.

(ii)\enspace
For $f,g\in\operatorname{CoDer}^{\mathrm{cyc}}$, the
commutator $[f,g] = f\circ g - (-1)^{|f||g|}g\circ f$ satisfies
the cyclic identity
\begin{align*}
\eta([f,g](x),y) &= \eta(f(g(x)),y) -
(-1)^{|f||g|}\eta(g(f(x)),y)\\
&= -(-1)^{|f|(|g|+|x|)}\eta(g(x),f(y))
 + (-1)^{|f||g|+|g||x|}\eta(f(x),g(y))\\
&= -(-1)^{(|f|+|g|)|x|}\eta(x,[f,g](y)),
\end{align*}
using the cyclic property of~$f$ and~$g$ in the second step and
regrouping signs. Hence $[f,g]$ is cyclic.

(iii)\enspace
The bar differential $d_{\barB}$ is a coderivation determined by
the chiral multiplication and higher operations of~$\cA$.
The cyclicity of $d_{\barB}$ is equivalent to the invariance of
$\langle{-},{-}\rangle_{\cA}$ under the chiral operations:
for the leading term,
$\langle m_2(a,b),c\rangle_{\cA}
= -(-1)^{|a||b|}\langle m_2(b,a),c\rangle_{\cA}
= \langle a, m_2(b,c)\rangle_{\cA}$,
and the higher-order terms satisfy the same identity by the
$A_\infty$ compatibility of the invariant form.

(iv)\enspace Parts~(ii) and~(iii) together make
$\operatorname{CoDer}^{\mathrm{cyc}}[1]$ a cyclic dg Lie algebra
in the sense of Kontsevich--Soibelman~\cite{KontsevichSoibelman}:
$l_1 = [d_{\barB},-]$ is skew because $d_{\barB}$ is cyclic and
the bracket is $\eta$-invariant, while $l_2 = [-,-]$ is invariant
by~(ii). The $(-1)$-shifted symplectic structure on the
Maurer--Cartan formal moduli problem is then the standard
consequence (cf.\ Loday--Vallette~\cite{LV12}, \S10.4).
\end{proof}

\begin{proposition}[Killing cocycle \texorpdfstring{$L_\infty$}{L-infinity} extension;
\ClaimStatusProvedHere]\label{prop:killing-linf-extension}
\index{Killing cocycle!$L_\infty$ extension}
\index{$L_\infty$-algebra!Killing cocycle extension}
Let $\mathfrak{g}$ be a finite-dimensional Lie algebra with
non-degenerate invariant symmetric bilinear form~$\kappa_{\mathfrak{g}}$.
Define the Killing $3$-cocycle
$\phi(a,b,c) := \kappa_{\mathfrak{g}}([a,b],c) \in \Lambda^3(\mathfrak{g}^*)$.
Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\phi$ is a Chevalley--Eilenberg $3$-cocycle:
 $\delta\phi = 0$.
\item The data $l_1 = 0$, $l_2 = [-,-]$,
 $l_3 = \phi$ \textup{(}valued in a one-dimensional marker
 direction~$\eta$\textup{)},
 and $l_n = 0$ for $n \geq 4$ defines an $L_\infty$-algebra
 structure on $\mathfrak{g} \oplus \mathbb{C}\cdot\eta$,
 where $\deg(\mathfrak{g}) = 0$ and $\deg(\eta) = 2$.
\item The pairing $\kappa_{\mathfrak{g}}$ on~$\mathfrak{g}$ extended by
 $\langle\eta,\eta\rangle = 1$ and
 $\langle\mathfrak{g},\eta\rangle = 0$ makes this a
 \emph{cyclic} $L_\infty$-algebra: $l_2$ is
 $\kappa_{\mathfrak{g}}$-invariant, the $4$-form
 $\langle l_3(a,b,c), d\rangle$ vanishes on
 $\mathfrak{g}^{\otimes 4}$, and the restriction
 $\langle l_3(a,b,c),\eta\rangle = \phi(a,b,c)$ is
 totally antisymmetric.
\end{enumerate}
\end{proposition}

\begin{proof}
(i)\enspace
The CE~differential of~$\phi$ evaluates as
\begin{align*}
(\delta\phi)(a,b,c,d)
&= \textstyle\sum_{i<j}(-1)^{i+j}\,
 \phi([x_i,x_j],x_k,x_l) \\
&= \textstyle\sum_{i<j}(-1)^{i+j}\,
 \kappa_{\mathfrak{g}}([[x_i,x_j],x_k],x_l).
\end{align*}
Using ad-invariance $\kappa_{\mathfrak{g}}([u,v],w) = \kappa_{\mathfrak{g}}(u,[v,w])$
repeatedly, this equals
$2\bigl(\kappa_{\mathfrak{g}}([a,c],[b,d]) - \kappa_{\mathfrak{g}}([a,b],[c,d])
 - \kappa_{\mathfrak{g}}([a,d],[b,c])\bigr)$.
Applying ad-invariance once more:
$\kappa_{\mathfrak{g}}([a,c],[b,d]) - \kappa_{\mathfrak{g}}([a,b],[c,d])
 - \kappa_{\mathfrak{g}}([a,d],[b,c])
= \kappa_{\mathfrak{g}}\bigl(a,\,
 [c,[b,d]] - [b,[c,d]] - [d,[b,c]]\bigr) = 0$
by the Jacobi identity $[b,[c,d]] + [c,[d,b]] + [d,[b,c]] = 0$.

(ii)\enspace
We verify the $L_\infty$ homotopy Jacobi identities at
each degree~$n$.

\emph{Degrees $1$--$3$.}
With $l_1 = 0$, degrees~$1$ and~$2$ hold trivially.
At degree~$3$, the identity reduces to the Jacobi identity
for~$l_2$, since the only $l_3$-involving term is
$l_1\circ l_3 = 0$.

\emph{Degree~$4$.}
The identity (with $l_1 = l_4 = 0$) reads
\begin{equation}\label{eq:degree4-linf}
\begin{split}
\textstyle\sum_{\sigma \in \mathrm{Sh}(1,3)}
 &\,\varepsilon(\sigma)\,l_2\bigl(x_{\sigma(1)},\,
 l_3(x_{\sigma(2)},x_{\sigma(3)},x_{\sigma(4)})\bigr)\\
&{}+ \textstyle\sum_{\sigma \in \mathrm{Sh}(2,2)}
 \varepsilon(\sigma)\,l_3\bigl(l_2(x_{\sigma(1)},
 x_{\sigma(2)}),\,x_{\sigma(3)},x_{\sigma(4)}\bigr) = 0.
\end{split}
\end{equation}
The first sum vanishes: $l_3$ outputs in the
$\eta$-direction and $l_2(x,\eta) = 0$ for all
$x \in \mathfrak{g}$. The second sum equals
$(\delta\phi)(a,b,c,d)\cdot\eta = 0$ by~(i).

\emph{Degrees $\geq 5$.}
With $l_n = 0$ for $n \geq 4$, every surviving term in the
degree-$n$ identity involves a composition
$l_3(\dots, l_3(\dots), \dots)$, which requires $l_3$ to
accept $\eta$ as input. Since $l_3$ is defined only on
$\mathfrak{g}^{\otimes 3}$, all such terms vanish.

(iii)\enspace
The bracket $l_2 = [-,-]$ is $\kappa_{\mathfrak{g}}$-invariant by the
ad-invariance of~$\kappa_{\mathfrak{g}}$
(Proposition~\ref{prop:genus0-cyclic-coderivation}(ii)).
For~$l_3$: on $\mathfrak{g}^{\otimes 4}$, the $4$-form
$\langle l_3(a,b,c),d\rangle = \phi(a,b,c)\langle\eta,d\rangle
= 0$ since $\langle\eta,\mathfrak{g}\rangle = 0$.
The restriction
$\langle l_3(a,b,c),\eta\rangle = \phi(a,b,c)$ inherits total
antisymmetry from the ad-invariance and antisymmetry
of~$\kappa_{\mathfrak{g}}\circ\mathrm{ad}$.
\end{proof}

\begin{corollary}[Kac--Moody cyclic deformation complex;
\ClaimStatusProvedHere]\label{cor:km-cyclic-deformation}
\index{Kac--Moody algebra!cyclic deformation complex}
For $\widehat{\mathfrak{g}}_k$ with $k\neq -h^\vee$ and
$\mathfrak{g}$ simple, the genus-$0$ cyclic deformation complex
$L_0 := \operatorname{CoDer}^{\mathrm{cyc}}(\bar{B}
(\widehat{\mathfrak{g}}_k))[1]$
of Proposition~\textup{\ref{prop:genus0-cyclic-coderivation}}
has the following explicit data:
\begin{enumerate}[label=\textup{(\roman*)}]
\item On generators, $l_2 = \mathrm{ad}$ \textup{(}adjoint
 bracket of~$\mathfrak{g}$\textup{)} and the cyclic pairing
 restricts to the level-$k$ Killing form
 $\kappa_k = k\,\kappa_{\mathfrak{g}} + \kappa_{\mathrm{Killing}}$.
\item The adjoint Casimir
 $C_2 = \sum_i \mathrm{ad}(e_i)\circ\mathrm{ad}(e^i)$
 acts as $2h^\vee\cdot\mathrm{id}$ on
 $s^{-1}\bar{\mathfrak{g}} \subset L_0$.
\item The unique cyclic infinitesimal deformation is
 the Killing $3$-cocycle
 $l_3(a,b,c) = \kappa_{\mathfrak{g}}([a,b],c)$, corresponding to the
 generator of $H^2_{\mathrm{cyc}}(\mathfrak{g},\mathfrak{g})
 \cong\mathbb{C}$
 \textup{(}Proposition~\textup{\ref{prop:cyclic-ce-identification}}\textup{)}.
\item The scalar shadow
 $\kappa(\widehat{\mathfrak{g}}_k) =
 \dim(\mathfrak{g})\,(k+h^\vee)/(2h^\vee)$
 is recovered from the $l_2$ bracket and the cyclic pairing via
 the two-channel decomposition
 \textup{(}Remark~\textup{\ref{rem:mc2-status}},
 items~\textup{(vi)--(ix)}\textup{)}.
\end{enumerate}
\end{corollary}

\begin{proof}
(i)\enspace
At genus~$0$, the PBW filtration identifies the generator-level
structure of~$L_0$ with the adjoint representation
of~$\mathfrak{g}$. The bar differential has leading term
$d_2(sa\,|\,sb) = s[a,b]$, so $l_2$ on generators is the adjoint
bracket. The invariant form on $\widehat{\mathfrak{g}}_k$ is
$\kappa_k$, which restricts to the level-$k$ normalized Killing
form on~$\mathfrak{g}$.

(ii)\enspace
On the adjoint representation, $C_2 = \sum_i \mathrm{ad}(e_i)
\circ\mathrm{ad}(e^i)$ has eigenvalue~$2h^\vee$ (standard: the
Casimir eigenvalue on the adjoint representation equals twice the
dual Coxeter number for simple~$\mathfrak{g}$).

(iii)\enspace
By Proposition~\ref{prop:cyclic-ce-identification},
$H^2_{\mathrm{cyc}}(\mathfrak{g},\mathfrak{g})\cong
H^3(\mathfrak{g})\cong\mathbb{C}$, generated by the Killing
$3$-cocycle $\phi(a,b,c)=\kappa_{\mathfrak{g}}([a,b],c)$. This is the unique
infinitesimal cyclic deformation direction: it defines
an~$l_3$ bracket on~$L_0$ satisfying all homotopy Jacobi
identities and cyclic symmetry by
Proposition~\ref{prop:killing-linf-extension}.
The computational verifications in
Remark~\ref{rem:mc2-status}, items~(v)--(vi),
(viii)--(ix) confirm this independently for
$\mathfrak{sl}_2$, $\mathfrak{sl}_3$,
$\mathfrak{sp}_4$, and~$\mathfrak{g}_2$.

(iv)\enspace
The two-channel decomposition extracts
$\kappa_{\mathrm{dp}}(\widehat{\mathfrak{g}}_k) = \dim(\mathfrak{g})\cdot k/(2h^\vee)$ from the
double-pole channel and $\dim(\mathfrak{g})/2$ from the
simple-pole channel. Their sum gives
$\kappa(\widehat{\mathfrak{g}}_k) = \kappa_{\mathrm{dp}}(\widehat{\mathfrak{g}}_k) + \dim(\mathfrak{g})/2
= \dim(\mathfrak{g})(k+h^\vee)/(2h^\vee)$, matching the
formula of Theorem~\ref{thm:modular-characteristic}.
\end{proof}

\begin{definition}[Cyclic deformation complex: bar-intrinsic
 form]
\label{def:cyclic-deformation-bar}
\index{cyclic deformation complex!bar-intrinsic form}
Let $\cA$ be a modular Koszul chiral algebra
(Definition~\ref{def:modular-koszul-chiral}) carrying the trace/duality
data needed to define the chain-level Verdier/BV pairing. The
\emph{bar-intrinsic cyclic deformation complex} is
\begin{equation}\label{eq:def-cyc-bar}
\Defcyc(\cA)
\;:=\;
\operatorname{CoDer}^{\mathrm{cyc}}\!\bigl(
 \widehat{\barB}_X(\cA)
\bigr)[1],
\end{equation}
the degree-shifted \emph{cyclic $L_\infty$-algebra} of continuous
cyclic coderivations of the completed reduced bar coalgebra
$\widehat{\barB}_X(\cA)$; ``cyclic'' means skew-adjoint for the
canonical pairing induced by Verdier duality/BV trace.
The $L_\infty$ structure has brackets $\ell_1 = [d_{\barB},-]$,
$\ell_2 = [-,-]$ (the coderivation bracket), and higher brackets
$\ell_n$ for $n \geq 3$ induced by the transferred $A_\infty$
structure on $\widehat{\barB}_X(\cA)$
\cite[Theorem~10.3.8]{LV12}.
For Koszul~$\cA$, the convolution $L_\infty$ is \emph{formal}
(the higher brackets $\ell_n = 0$ for $n \geq 3$ on the
cohomological model), so the strict dg~Lie structure suffices for
computations
(Theorem~\ref{thm:cyclic-linf-graph}).

Four properties:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Filtered-completeness:} the bar-length filtration makes
 $\Defcyc(\cA)$ complete and pronilpotent.
\item \emph{Functoriality:} the assignment $\cA \mapsto \Defcyc(\cA)$
 is functorial in morphisms of augmented chiral algebras.
\item \emph{Cyclic pairing:} the Verdier/BV trace induces a
 $(-1)$-shifted symplectic structure on the formal moduli problem
 $\operatorname{MC}(\Defcyc(\cA))$.
\item \emph{Curved MC control:} Maurer--Cartan elements of
 $\Defcyc(\cA)$ parametrize curved deformations of the bar
 differential, so the genus tower is controlled by a single MC
 deformation.
\end{enumerate}
The degree shift~$[1]$ makes the Lie bracket of degree~$0$, matching
the convention for tangent Lie algebras of formal moduli problems
(Lurie~\cite{HA}). Equivalently,
$\Defcyc(\cA)$ is the tangent dg Lie algebra of cyclic deformations
of~$\cA$ as a modular factorization algebra; it presents the abstract
H-level object of Definition~\ref{def:cyclic-deformation-elementary}
via bar-coalgebra coderivations.

\smallskip\noindent
\emph{Claim status.}
At genus~$0$, the cyclic coderivation complex is fully constructed
(Proposition~\ref{prop:genus0-cyclic-coderivation}), and its
Kac--Moody specialization is computed explicitly
(Corollary~\ref{cor:km-cyclic-deformation}).
\textbf{For affine Kac--Moody algebras}, $\Defcyc(\widehat{\mathfrak{g}}_k)$
is a well-defined cyclic $L_\infty$-algebra with
$H^2 \cong \mathbb{C}$: Theorem~\ref{thm:mc2-1-km} identifies the
coderivation differential with the cyclic CE~differential and proves
Hypothesis~\ref{mc2-hyp:cyclic} for this family.
The full modular extension for general modular Koszul chiral
algebras is now established by
Theorem~\ref{thm:cyclic-linf-graph}: the chiral graph complex
construction equips $\Defcyc(\cA)$ with a cyclic $L_\infty$
structure for all Koszul chiral algebras with non-degenerate
invariant form.
(Part of the MC2 theorem package; Theorem~\ref{thm:mc2-full-resolution}.)
\end{definition}

\begin{definition}[Modular cyclic deformation complex;
\ClaimStatusProvedHere]
\label{def:modular-cyclic-deformation-complex}
\index{modular cyclic deformation complex|textbf}
\index{cyclic deformation complex!modular extension}
For a chiral algebra~$\cA$ with bar
complex~$\barB(\cA)$, the \emph{modular cyclic deformation complex} is
\begin{equation}\label{eq:modular-cyc-def-complex}
\Defcyc^{\mathrm{mod}}(\cA)
\;:=\;
\prod_{\substack{g,n \\ 2g-2+n>0}}
\operatorname{CoDer}^{\mathrm{cyc}}\!\bigl(
 \barB^{(g,n)}(\cA)
\bigr)[1],
\end{equation}
where $\barB^{(g,n)}(\cA)$ is the genus-$g$, $n$-marked bar complex
and the product ranges over stable pairs~$(g,n)$.
The differential is the sum $d_{\mathrm{int}} + d_{\mathrm{sew}}$
where:
\begin{itemize}
\item $d_{\mathrm{int}}$ is the internal cyclic coderivation
 differential on each component;
\item $d_{\mathrm{sew}}$ is the clutching/sewing operation induced by
 the boundary maps
 $\partial\colon \overline{\mathcal{M}}_{g,n} \supset
 \Delta_{g_1,S_1;\,g_2,S_2} \to
 \overline{\mathcal{M}}_{g_1,|S_1|+1} \times
 \overline{\mathcal{M}}_{g_2,|S_2|+1}$.
\end{itemize}

The Lie bracket is \emph{graph composition}: for
$\xi \in \operatorname{CoDer}^{\mathrm{cyc}}(\barB^{(g_1,n_1)}(\cA))$
and
$\eta \in \operatorname{CoDer}^{\mathrm{cyc}}(\barB^{(g_2,n_2)}(\cA))$,
\begin{equation}\label{eq:modular-cyc-graph-bracket}
[\xi,\eta]
\;:=\;
\sum_{\Gamma}\xi \circ_\Gamma \eta,
\end{equation}
summed over stable graphs~$\Gamma$ connecting an output of~$\xi$ to an
input of~$\eta$ with cross-polarization on internal edges.
\end{definition}

\begin{remark}[Strictification of the modular deformation object]
\label{rem:modular-cyc-strictification}
The modular cyclic deformation complex $\Defcyc^{\mathrm{mod}}(\cA)$
is the strict model of the homotopy-invariant modular deformation
object $\Definfmod(\cA)$
\textup{(}Theorem~\textup{\ref{thm:modular-homotopy-convolution})}.
The cyclic coderivation description is one model, obtained from the
cofree resolution of~$\barB(\cA)$; a different choice of
contracting homotopy produces an $L_\infty$-quasi-isomorphic
deformation complex. For affine Kac--Moody algebras, the
strict model is already formal: the universal class
$\Theta^{\mathrm{str}}_{\widehat{\mathfrak{g}}_k}$ satisfies the strict
MC equation with all higher $L_\infty$-brackets vanishing
\textup{(}Theorem~\textup{\ref{thm:km-strictification})}.
\end{remark}

\begin{proposition}[Genus truncation;
\ClaimStatusProvedHere]
\label{prop:modular-deformation-truncation}
\index{modular cyclic deformation complex!genus truncation}
The genus-$0$ truncation
$\Defcyc^{\mathrm{mod}}(\cA)\big|_{g=0} = \Defcyc(\cA)$
recovers the elementary cyclic deformation complex of
Definition~\textup{\ref{def:cyclic-deformation-bar}}.
The genus grading induces a complete descending filtration
$F^{\bullet}\Defcyc^{\mathrm{mod}}(\cA)$ with
$\gr_g$ computing deformations at fixed genus.
\end{proposition}

\begin{proof}
At $g = 0$ the only stable pairs are $(0,n)$ with $n \geq 3$.
The internal differential~$d_{\mathrm{int}}$ on each
$\operatorname{CoDer}^{\mathrm{cyc}}(\barB^{(0,n)}(\cA))[1]$
coincides with the coderivation differential of
Definition~\ref{def:cyclic-deformation-bar}, and the sewing
differential~$d_{\mathrm{sew}}$ reduces to the graph composition
already present in the genus-$0$ bracket.
The genus filtration $F^g := \prod_{h \geq g}$ is complete because
the product topology is, and the associated graded
$\gr_g = \operatorname{CoDer}^{\mathrm{cyc}}(\barB^{(g,\bullet)}(\cA))[1]$
computes deformations at fixed genus by construction.
\end{proof}

\begin{remark}[Modular cyclic deformation complex as MC ambient]
\label{rem:chriss-ginzburg-modular-cyc}
\index{Chriss--Ginzburg principle}
\index{Maurer--Cartan!modular cyclic}
The modular cyclic deformation complex is the ambient home for
$\Theta_\cA$. At the dg~level,
the Lie bracket and differential give a cyclic dg~Lie algebra;
Theorem~\ref{thm:cyclic-linf-graph} extends this to a full
\emph{cyclic $L_\infty$-algebra}, and
Theorem~\ref{thm:modular-quantum-linfty} promotes it to a
\emph{quantum $L_\infty$-algebra} with operations
$\{\ell_n^{(g)}\}_{n \geq 1,\, g \geq 0}$: here
$\ell_1^{(0)} = D$, $\ell_2^{(0)} = [-,-]$,
$\ell_n^{(0)}$ for $n \geq 3$ are the higher operadic brackets from
homotopy transfer through $C_*(\overline{\mathcal{M}}_{0,n+1})$
(Loday--Vallette~\cite[Thm~10.3.8]{LV12}), and
$\ell_n^{(g)}$ for $g \geq 1$ are the higher-genus Feynman
amplitudes from stable-graph sums of type~$(g,n)$
(Getzler--Kapranov~\cite[\S5]{GeK98},
Chuang--Lazarev~\cite{CL10}).

The modular MC problem: find
$\Theta_\cA \in \MC(\Defcyc^{\mathrm{mod}}(\cA))$ satisfying the
quantum $L_\infty$ Maurer--Cartan equation
\[
\sum_{n \geq 1} \frac{1}{n!}\,\ell_n^{(0)}
 (\Theta_\cA,\dots,\Theta_\cA)
\;+\;
\sum_{g \geq 1} \hbar^{g}\,
 \ell_1^{(g)}(\Theta_\cA)
\;=\; 0,
\]
whose leading terms $\ell_1^{(0)}(\Theta) + \tfrac{1}{2}\ell_2^{(0)}(\Theta,\Theta) = 0$ give
the classical dg~MC equation
$d\Theta_\cA + \tfrac{1}{2}[\Theta_\cA, \Theta_\cA] = 0$,
the strict shadow of the full $L_\infty$-MC equation
(Theorem~\ref{thm:modular-homotopy-convolution}).
Theorem~\ref{thm:universal-MC} establishes existence of~$\Theta_\cA$
for Kac--Moody at non-critical level,
Virasoro, and principal~$\mathcal{W}_N$ at generic level.
All modular invariants ($\kappa$, $\Delta$, shadows
$\operatorname{Sh}_r$) are projections of~$\Theta_\cA$ onto graded
components; the higher brackets $\ell_n^{(g)}$ encode
the Feynman-amplitude content beyond the leading dg~terms.
\end{remark}

\begin{proposition}[Hochschild as degree-$2$ shadow projection;
\ClaimStatusProvedHere]
\label{prop:hochschild-shadow-projection}
\index{chiral Hochschild cohomology!shadow projection}
\index{shadow algebra!degree-2 projection}

The chiral Hochschild cohomology of a modular Koszul algebra $\cA$ is
the degree-$2$ projection of the shadow algebra:
\[
\mathrm{ChirHoch}^n(\cA) \;\cong\;
\cA^{\mathrm{sh}}_{2,0}{}^n \;=\;
H^n\bigl(\pi_{2,0}(\Defcyc^{\mathrm{mod}}(\cA))\bigr).
\]
Polynomial growth of $\mathrm{ChirHoch}^*(\cA)$ is equivalent to the
vanishing $\cA^{\mathrm{sh}}_{r,0} = 0$ for $r \geq 3$ at genus~$0$,
i.e., to chiral Koszulness.
\end{proposition}

\begin{proof}
The degree-$2$, genus-$0$ component
$\pi_{2,0}(\Defcyc^{\mathrm{mod}}(\cA))$ computes binary
cyclic coderivations of the bar complex, which is the Hochschild
cochain complex of~$\cA$
(Theorem~\ref{thm:main-koszul-hoch}).
The equivalence with Koszulness follows from
Theorem~\ref{thm:koszul-equivalences-meta}\textup{(iii)}:
$A_\infty$-formality is the vanishing of genus-$0$ shadows
at degree~$\geq 3$.
\end{proof}

\begin{theorem}[MC2-1 for Kac--Moody algebras;
\ClaimStatusProvedHere]\label{thm:mc2-1-km}
\index{MC2!Kac--Moody resolution}
For $\widehat{\mathfrak{g}}_k$ at non-critical level ($k \neq -h^\vee$)
with $\mathfrak{g}$ simple, Hypothesis~\textup{\ref{mc2-hyp:cyclic}}
is satisfied:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Cyclic $L_\infty$ structure.}
 The bar-intrinsic cyclic deformation complex
 \[
 \Defcyc(\widehat{\mathfrak{g}}_k)
 := \operatorname{CoDer}^{\mathrm{cyc}}(\widehat{\barB}_X
 (\widehat{\mathfrak{g}}_k))[1]
 \]
 is a well-defined complete cyclic $L_\infty$-algebra
 \textup{(}a fortiori: a cyclic dg~Lie algebra\textup{)}.

\item \emph{CE identification.}
 The coderivation differential $l_1 = [d_{\barB},-]$ is canonically
 identified with the cyclic Chevalley--Eilenberg differential:
 \begin{equation}\label{eq:coder-ce-ident}
 \bigl(\Defcyc(\widehat{\mathfrak{g}}_k),\, l_1\bigr)
 \;\cong\;
 \bigl(C^{*-1}_{\mathrm{cyc}}(\mathfrak{g},\mathfrak{g}),\,
 \delta_{\mathrm{CE}}\bigr).
 \end{equation}
 In particular,
 $H^n(\Defcyc(\widehat{\mathfrak{g}}_k), l_1) \cong
 H^n_{\mathrm{cyc}}(\mathfrak{g},\mathfrak{g})$
 for all $n \geq 0$.

\item \emph{One-dimensional obstruction.}
 $H^2(\Defcyc(\widehat{\mathfrak{g}}_k), l_1) \cong \mathbb{C}$,
 generated by the Killing $3$-cocycle
 $\phi(a,b,c) = \kappa([a,b],c)$.
\end{enumerate}
\end{theorem}

\begin{proof}
(i)\enspace
By Proposition~\ref{prop:genus0-cyclic-coderivation},
$\operatorname{CoDer}^{\mathrm{cyc}}(\barB(\widehat{\mathfrak{g}}_k))[1]$
is a cyclic dg Lie algebra.
The bar coalgebra $\barB = T^c(s^{-1}\bar{\mathfrak{g}})$ is
conilpotent, and its bar-length filtration is complete and separated.
Continuous coderivations of the completed bar coalgebra
$\widehat{\barB}$ are determined by their bar-length components
$f_p\colon (s^{-1}\bar{\mathfrak{g}})^{\otimes p}
\to s^{-1}\bar{\mathfrak{g}}$, forming the product
$\prod_{p \geq 1}
\operatorname{Hom}^{\mathrm{cyc}}
((s^{-1}\bar{\mathfrak{g}})^{\otimes p},\,
s^{-1}\bar{\mathfrak{g}})$.
The bracket of a bar-length-$p$ and a bar-length-$q$ coderivation
has bar-length $p + q - 1$ (by the pre-Lie composition formula),
and the cyclic pairing~$\eta$ pairs bar-length~$p$ with
bar-length~$p$; both converge in the completed product.
A cyclic dg~Lie algebra is in particular a cyclic
$L_\infty$-algebra (with $l_n = 0$ for $n \geq 3$).

(ii)\enspace
The reduced bar differential of $\widehat{\mathfrak{g}}_k$ on
$\barB = T^c(s^{-1}\bar{\mathfrak{g}})$ has cogeneration components
$d_n\colon (s^{-1}\bar{\mathfrak{g}})^{\otimes n}
\to s^{-1}\bar{\mathfrak{g}}$.
Only $d_2$ is nonzero: $d_2(a,b) = [a,b]$ encodes the simple-pole
OPE $J^a(z)J^b(w) \sim f^{ab}_c J^c/(z{-}w)$, while the double-pole
data $k\kappa^{ab}/(z{-}w)^2$ maps to the vacuum (augmentation
sector) and does not contribute to the \emph{reduced} bar
differential; higher poles are absent for affine Kac--Moody.

For a coderivation $f = (f_p)_{p \geq 1}$ and the bar differential
$d_{\barB}$ with sole component~$d_2$, the pre-Lie composition
formula gives:
\[
[d_2, f_p]
\;=\; d_2 \circ f_p \;-\; (-1)^{|d_2||f_p|}\, f_p \circ d_2,
\]

which has bar-length $p + 2 - 1 = p + 1$. Hence $l_1 = [d_{\barB},-]$
maps bar-length-$p$ to bar-length-$(p{+}1)$, with no bar-length-lowering
terms. Explicitly, on a bar-length-$p$ cyclic map
$f_p\colon (s^{-1}\bar{\mathfrak{g}})^{\otimes p}
\to s^{-1}\bar{\mathfrak{g}}$:
\begin{align*}
(d_2 \circ f_p)(a_1, \ldots, a_{p+1})
&= \sum_{i=1}^{p} \varepsilon_i\,
 [f_p(a_1, \ldots, \widehat{a}_i, \ldots, a_{p+1}),\, a_i], \\
(f_p \circ d_2)(a_1, \ldots, a_{p+1})
&= \sum_{i < j} \varepsilon_{ij}\,
 f_p(a_1, \ldots, [a_i, a_j], \ldots, \widehat{a}_j,
 \ldots, a_{p+1}),
\end{align*}

where $\varepsilon_i, \varepsilon_{ij}$ are the standard Koszul signs.
These are exactly the two terms of the Chevalley--Eilenberg differential
$\delta_{\mathrm{CE}}$ on
$C^p_{\mathrm{cyc}}(\mathfrak{g},\mathfrak{g})
= \operatorname{Hom}^{\mathrm{cyc}}
((s^{-1}\bar{\mathfrak{g}})^{\otimes p},\,
s^{-1}\bar{\mathfrak{g}})$,
with the cyclic-invariance property preserved because $d_2 = [-,-]$
is $\kappa$-invariant (Proposition~\ref{prop:genus0-cyclic-coderivation}(iii)).
The identification~\eqref{eq:coder-ce-ident} follows.

(iii)\enspace
By Proposition~\ref{prop:cyclic-ce-identification},
$H^n_{\mathrm{cyc}}(\mathfrak{g},\mathfrak{g})
\cong H^{n+1}(\mathfrak{g})$.
For simple~$\mathfrak{g}$, $H^3(\mathfrak{g}) = \mathbb{C}$,
generated by the Killing $3$-form
$\phi(a,b,c) = \kappa([a,b],c) \in \Lambda^3(\mathfrak{g}^*)$.
Under the isomorphism of~(ii), this corresponds to the
unique cyclic infinitesimal deformation direction
(Corollary~\ref{cor:km-cyclic-deformation}(iii)).
\end{proof}

\begin{corollary}[Minimal cyclic \texorpdfstring{$L_\infty$}{L-infinity} model for Kac--Moody;
\ClaimStatusProvedHere]\label{cor:km-minimal-linf}
\index{minimal model!Kac--Moody cyclic $L_\infty$}
Theorem~\textup{\ref{thm:mc2-1-km}} and the homotopy transfer
theorem for cyclic $L_\infty$-algebras
\textup{(}Kontsevich--Soibelman~\textup{\cite{KontsevichSoibelman}},
Loday--Vallette~\textup{\cite{LV12}} \S10.3\textup{)}
give a minimal cyclic $L_\infty$ model for
$\Defcyc(\widehat{\mathfrak{g}}_k)$ on the cohomology
$H^*(\Defcyc, l_1) \cong \mathfrak{g} \oplus \mathbb{C}\cdot\eta$
\textup{(}degrees $0$ and~$2$\textup{)}.
The transferred structure is exactly
the Killing cocycle extension of
Proposition~\textup{\ref{prop:killing-linf-extension}}:
\begin{equation}\label{eq:km-minimal-linf-structure}
l_2^{\mathrm{tr}} = [-,-]_{\mathfrak{g}},\quad
l_3^{\mathrm{tr}} = \phi,\quad
l_n^{\mathrm{tr}} = 0 \;\text{for}\; n \geq 4.
\end{equation}
\end{corollary}

\begin{proof}
The homotopy transfer theorem produces a minimal $L_\infty$-algebra
$(H^*(\Defcyc, l_1),\, l_n^{\mathrm{tr}})$ quasi-isomorphic to the
original cyclic dg~Lie algebra. By
Theorem~\ref{thm:mc2-1-km}(ii), $H^0 \cong \mathfrak{g}$ (the
adjoint representation) and $H^2 \cong \mathbb{C}$.

\emph{$l_2^{\mathrm{tr}} = \mathrm{ad}$.}
The transferred binary bracket $l_2^{\mathrm{tr}}(a,b) =
p\,l_2(i(a), i(b))$, where $i\colon \mathfrak{g} \hookrightarrow
\Defcyc$ is the inclusion into bar-length~$1$ and $p$ is the
projection. Since bar-length-$1$ coderivations are linear
endomorphisms and $l_2$ is the commutator, $l_2^{\mathrm{tr}}(a,b)
= [a,b]$.

\emph{$l_3^{\mathrm{tr}} = \phi$.}
The transferred ternary bracket on $\mathfrak{g}^{\otimes 3}$
lands in $H^2 \cong \mathbb{C}\cdot\eta$, so it defines an element of
$\operatorname{Hom}(\Lambda^3(\mathfrak{g}),\, \mathbb{C})
\cong H^3(\mathfrak{g}) = \mathbb{C}$.
The homotopy transfer formula
$l_3^{\mathrm{tr}}(a,b,c) = p\,l_2(h\,l_2(i(a),i(b)),\, i(c))
+ \text{(cyclic)}$
is an explicit $3$-cocycle on~$\mathfrak{g}$, hence proportional
to~$\phi$. It is nonzero because the contracting homotopy~$h$
maps the bar-length-$2$ image of $l_2(i(a),i(b))$, which carries
the Killing-form data via the cyclic pairing, nontrivially
into the obstruction direction.
Normalizing the generator of~$H^2$ to agree with
Proposition~\ref{prop:killing-linf-extension}
gives $l_3^{\mathrm{tr}} = \phi$.

\emph{$l_n^{\mathrm{tr}} = 0$ for $n \geq 4$.}
For $n = 4$: the transfer formula
(Loday--Vallette \cite{LV12} Theorem~10.3.1) gives
$l_4^{\mathrm{tr}}$ as a composite of $l_2^{\mathrm{tr}}, l_3^{\mathrm{tr}}$
and the homotopy~$h$. Every such composite lands in
$H^2 \cong \mathbb{C}\cdot\eta$, and composing further with
$l_2^{\mathrm{tr}}$ on this $1$-dimensional space vanishes
(since $\eta \notin \mathfrak{g}$). Equivalently, the degree-$4$
homotopy Jacobi identity $\partial l_3^{\mathrm{tr}} +
\{l_2^{\mathrm{tr}}, l_4^{\mathrm{tr}}\} = 0$ combined with
$\partial l_3^{\mathrm{tr}} = \delta\phi = 0$
(Proposition~\ref{prop:killing-linf-extension}(i)) forces
$l_4^{\mathrm{tr}} = 0$.
For $n \geq 5$: every tree in the transfer formula with $n$ leaves
must route at least one input through $H^2 \cong \mathbb{C}\cdot\eta$;
since $l_3^{\mathrm{tr}}$ requires all three inputs in~$\mathfrak{g}$
and $\eta \notin \mathfrak{g}$, the composite vanishes.
\end{proof}

\begin{remark}[Scope of Theorem~\ref{thm:mc2-1-km}]
\label{rem:mc2-1-km-scope}
This resolves Hypothesis~\ref{mc2-hyp:cyclic} for
$\widehat{\mathfrak{g}}_k$ at non-critical levels; all three MC2
hypotheses are now resolved by
Theorem~\ref{thm:mc2-full-resolution}. The minimal model
(Corollary~\ref{cor:km-minimal-linf}) gives the Killing extension,
verified computationally in Remark~\ref{rem:mc2-status}(v)--(ix).
\end{remark}

\begin{remark}[Why introduce \texorpdfstring{$\operatorname{Def}_{\mathrm{cyc}}$}{Def_cyc}
now]\label{rem:def-cyc-role}
The genus tower, curvature scalars $\mcurv{g}$, and obstruction
classes are all shadows of the shadow obstruction tower
$\Theta_\cA^{\leq r}$
(Definition~\ref{def:shadow-postnikov-tower})
in $\operatorname{Def}_{\mathrm{cyc}}(\cA) \widehat{\otimes}
R\Gamma(\overline{\mathcal{M}}_{g,\bullet}, \mathbb{Q})$;
at the scalar level (Theorem~\ref{thm:explicit-theta}):
$\Theta_\cA^{\leq 2} = \kappa(\cA) \cdot \eta \otimes \Lambda$
(here $\Theta_\cA^{\leq 2}$ is \emph{proved} for all Koszul families;
the full tower $\Theta_\cA = \varprojlim_r \Theta_\cA^{\leq r}$
exists by the bar-intrinsic construction;
see Theorem~\ref{thm:mc2-bar-intrinsic}).
The MC2 extension problem is packaged by
Proposition~\ref{prop:mc2-reduction-principle} into three tasks;
the clutching package is resolved by
Proposition~\ref{prop:geometric-modular-operadic-mc}, and the
surviving one-channel obstruction is further reduced through a
sequence of propositions
(\ref{prop:tautological-line-support-criterion}--\ref{prop:one-channel-normalization-criterion})
to a normalized scalar comparison.
\end{remark}

\subsection{The chiral graph complex and cyclic
\texorpdfstring{$L_\infty$}{L-infinity} structure}
\label{subsec:chiral-graph-complex}
\index{graph complex!chiral}
\index{cyclic $L_\infty$-algebra!graph complex construction}

The dg Lie algebra $\Defcyc(\cA)$ of
Proposition~\ref{prop:genus0-cyclic-coderivation} is the genus-$0$ shadow
of a cyclic $L_\infty$-algebra whose higher
brackets $l_n$ ($n \geq 3$) arise from sums over chiral
graphs. This adapts the Kontsevich--Soibelman
construction~\cite{KontsevichSoibelman} to chiral algebras on algebraic
curves via configuration space integrals on
Fulton--MacPherson compactifications.

\begin{definition}[Chiral graphs]\label{def:chiral-graph}
\index{chiral graph}
A \emph{chiral graph} of type $(n, L)$ is a datum
$\Gamma = (V_{\mathrm{ext}}, V_{\mathrm{int}}, E, \sigma)$ where:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $V_{\mathrm{ext}} = \{v_1, \ldots, v_n\}$ is an ordered set of
 $n$~\emph{external vertices} (legs);
\item $V_{\mathrm{int}}$ is a finite set of \emph{internal vertices},
 each of valence $\geq 3$;
\item $E$ is a set of edges connecting vertices in
 $V = V_{\mathrm{ext}} \sqcup V_{\mathrm{int}}$, with the graph
 $(V, E)$ connected;
\item $\sigma$ is a cyclic ordering of the half-edges at each internal
 vertex (ribbon structure);
\item the loop number is $L = |E| - |V| + 1$.
\end{enumerate}
The automorphism group $\operatorname{Aut}(\Gamma)$ consists of
graph automorphisms preserving the external vertex labeling and the
ribbon structure. Let $\mathfrak{G}_{n,L}$ denote the set of
isomorphism classes of chiral graphs of type $(n, L)$.
\end{definition}

\begin{definition}[Graph amplitude]\label{def:graph-amplitude}
\index{graph amplitude!chiral}
Let $\cA$ be a Koszul chiral algebra on a smooth projective curve~$X$
with non-degenerate invariant form
$\langle{-},{-}\rangle_{\cA}\colon \cA\otimes\cA\to\omega_X$,
and let $S(z,w)$ denote the Szeg\H{o} kernel on~$X$: the unique
section of
$\omega_X^{1/2} \boxtimes \omega_X^{1/2}(\Delta)$
with a simple pole along the diagonal and no other singularities.

For a chiral graph $\Gamma \in \mathfrak{G}_{n,L}$ and cyclic
coderivations $f_1, \ldots, f_n \in
\operatorname{CoDer}^{\mathrm{cyc}}(\barB_X(\cA))$, the
\emph{graph amplitude} is
\begin{equation}\label{eq:graph-amplitude}
w_\Gamma(f_1, \ldots, f_n)
\;:=\;
\int_{\ConfigSpace{|V_{\mathrm{int}}|}}
\biggl(\prod_{e = (v_a, v_b) \in E_{\mathrm{int}}}
 S(z_a, z_b)\biggr)
\,\biggl(\prod_{i=1}^{n} \iota_{v_i}(f_i)\biggr)
\,\biggl(\prod_{v \in V_{\mathrm{int}}} m_{\mathrm{val}(v)}\biggr),
\end{equation}

where:

\begin{itemize}
\item $\ConfigSpace{|V_{\mathrm{int}}|}$ is the Fulton--MacPherson
 compactification of the configuration of internal vertex positions
 on~$X$;
\item $E_{\mathrm{int}} \subset E$ is the set of internal edges
 (both endpoints in $V_{\mathrm{int}}$);
\item $\iota_{v_i}(f_i)$ inserts the coderivation $f_i$ at the
 external vertex~$v_i$ via the bar-length projection
 $\operatorname{pr}_1\colon T^c(s^{-1}\bar{\cA}) \to
 s^{-1}\bar{\cA}$;
\item $m_{\mathrm{val}(v)}$ is the $A_\infty$ operation of
 degree $\mathrm{val}(v)$ at each internal vertex~$v$, contracted
 with $\langle{-},{-}\rangle_{\cA}$ along each internal edge;
\item signs follow the Koszul convention determined by the ribbon
 structure of~$\Gamma$
 (Appendix~\ref{app:signs}, \S\ref{app:sign-conventions}).
\end{itemize}
When $V_{\mathrm{int}} = \emptyset$ (all vertices external), the
integral is absent and the amplitude is a direct algebraic contraction.
\end{definition}

\begin{construction}[$L_\infty$ brackets from graph
sums]\label{constr:linf-from-graphs}
\index{$L_\infty$-algebra!graph sum construction}
Define the $n$-ary bracket on
$\Defcyc(\cA) = \operatorname{CoDer}^{\mathrm{cyc}}(\barB_X(\cA))[1]$
by
\begin{equation}\label{eq:linf-graph-sum}
l_n(f_1, \ldots, f_n)
\;:=\;
\sum_{\Gamma \in \mathfrak{G}_{n,0}}
\frac{(-1)^{\epsilon(\Gamma)}}
{\lvert\operatorname{Aut}(\Gamma)\rvert}
\, w_\Gamma(f_1, \ldots, f_n),
\end{equation}
where the sum runs over \emph{tree-level} chiral graphs ($L = 0$) with
$n$~external legs, and $\epsilon(\Gamma)$ is the sign from the
canonical orientation of~$\Gamma$ determined by the ribbon structure
and edge ordering.
\end{construction}

The graph sum~\eqref{eq:linf-graph-sum} is well-defined for Koszul
chiral algebras:
(a)~$\mathfrak{G}_{n,0}$ is finite at each degree~$n$ (a tree on $n + k$ vertices with $n$~external legs has
$k$~internal vertices, and valence~$\geq 3$ forces
$k \leq n - 2$);
(b)~the integrals over~$\ConfigSpace{k}$ converge by
regularity of forms on the FM~compactification;
(c)~the bar-length filtration makes the sum locally finite in each
filtered degree.

\begin{proposition}[Fay trisecant identity for the Szeg\H{o} kernel {\cite[Corollary~2.5]{Fay73}};
\ClaimStatusProvedElsewhere]\label{prop:fay-trisecant}
\index{Fay trisecant identity}
\index{Szeg\H{o} kernel!Fay identity}
Let $X$ be a smooth projective curve of genus~$g \geq 0$ and
$S(z,w)$ the Szeg\H{o} kernel on~$X$: the unique section of
$\omega_X^{1/2} \boxtimes \omega_X^{1/2}(\Delta)$ with simple pole
along the diagonal and no other singularities. Then on the
configuration space $C_3(X)$:
\begin{equation}\label{eq:algebraic-fay}
S(z_1, z_2)\,S(z_2, z_3) + S(z_2, z_3)\,S(z_3, z_1) +
S(z_3, z_1)\,S(z_1, z_2) \;=\; 0.
\end{equation}
At genus~$0$, this reduces to the partial-fraction identity for
$1/(z_1-z_2)(z_2-z_3)$.
\end{proposition}

\begin{proof}
This is the trisecant identity of Fay~\cite[Corollary~2.5]{Fay73},
proved via the addition formula for theta functions on~$X$.
The identity holds at all genera: the Szeg\H{o} kernel is
constructed from the prime form~$E(z,w)$ and the theta function
$\vartheta$ of any odd characteristic, and the three-term relation
follows from the Riemann identity for products of theta functions.
\end{proof}

\begin{proposition}[Stokes regularity for graph amplitudes on FM
compactifications;
\ClaimStatusProvedHere]\label{prop:stokes-regularity-FM}
\index{FM compactification!Stokes regularity}
\index{graph amplitude!boundary regularity}
Let $X$ be a smooth projective curve, $\cA$ a Koszul chiral algebra
on~$X$ with non-degenerate invariant form, and
$\omega_\Gamma \in \Omega^*(\ConfigSpace{k})$
a graph amplitude form~\eqref{eq:graph-amplitude} for a chiral
graph~$\Gamma$ with $k$~internal vertices. Then:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Logarithmic regularity.}
 The form $\omega_\Gamma$ extends to a form with at most logarithmic
 singularities along the boundary divisors $D_S \subset
 \ConfigSpace{k}$
 \textup{(}$S \subset \{1,\ldots,k\}$, $|S|\geq 2$\textup{)}.
 In particular, $\omega_\Gamma$ is locally integrable on
 $\ConfigSpace{k}$.
\item \emph{Stokes identity.}
 \begin{equation}\label{eq:stokes-FM}
 \int_{\ConfigSpace{k}} d\omega_\Gamma
 \;=\;
 \sum_{S} \int_{D_S} \omega_\Gamma,
 \end{equation}
 where the sum runs over boundary divisors.
\item \emph{Boundary correspondence.}
 The restriction of $\omega_\Gamma$ to the boundary divisor
 $D_S \cong \ConfigSpace{|S|} \times \ConfigSpace{k-|S|+1}$
 computes the product of graph amplitudes obtained by collapsing
 the subset~$S$ to a single vertex.
\end{enumerate}
\end{proposition}

\begin{proof}
\emph{(a) Logarithmic regularity.}
The FM compactification $\ConfigSpace{k}$ is a smooth algebraic
variety with simple normal crossing boundary
divisor~\cite{FM94}. The graph amplitude form $\omega_\Gamma$ is a
product of Szeg\H{o} propagators $S(z_a, z_b)$, one per internal
edge, contracted with $A_\infty$ operations and the invariant form
of~$\cA$. Each factor $S(z_a, z_b)$ is a section of
$\omega_X^{1/2} \boxtimes \omega_X^{1/2}(\Delta_{ab})$
with a simple pole along the diagonal $\Delta_{ab}$.

In the FM compactification, the diagonal $\Delta_{ab}$ is replaced
by the exceptional divisor $D_{\{a,b\}}$. In the local coordinates
$(r_S, \theta_S)$ of the FM blowup at $D_S$
\cite[§2]{FM94}, the propagator has the expansion
$S(z_a, z_b) = r_S^{-1} \cdot \phi_S + O(1)$ where $\phi_S$ is a
smooth section on $D_S$. This is a log pole:
$S(z_a,z_b) \, dz_a$ contributes $dr_S/r_S$ (a log
$1$-form) plus smooth terms. Hence the product over edges gives a
form with logarithmic poles along each $D_S$ meeting the graph's
edges, precisely a section of $\Omega^*(\log D)$ on
$\ConfigSpace{k}$, where $D = \bigcup_S D_S$.

\emph{(b) Stokes identity.}
For log forms on a smooth variety with simple normal crossing
boundary divisor, the residue form of Stokes' theorem holds:
$\int d\omega = \sum_S \int_{D_S} \operatorname{Res}_{D_S} \omega$.
This is the content of the Leray residue calculus for log de~Rham
complexes~\cite{Deligne70}. Alternatively, the real-analytic
version follows from Stokes' theorem on manifolds with corners
applied to the real-oriented blowup of
$\ConfigSpace{k}$~\cite{AS94}, as used in Chern--Simons
perturbation theory. The application to configuration-space
integrals with propagator insertions is carried out
in~\cite{Kon03} and~\cite{costello-renormalization}.

\emph{(c) Boundary correspondence.}
When the subset $S = \{z_{a_1}, \ldots, z_{a_s}\}$ of internal
vertex positions collide, the FM blowup produces the exceptional
divisor $D_S \cong \ConfigSpace{|S|} \times \ConfigSpace{k-|S|+1}$,
where the first factor parametrizes the relative positions of the
colliding points and the second parametrizes the remaining
configuration with $S$ collapsed to a single point~\cite[§3]{FM94}.
The residue of $\omega_\Gamma$ along $D_S$ localizes the
propagators within $S$: the edges internal to $S$ contribute the
graph amplitude of the subgraph $\Gamma|_S$, while the edges
connecting $S$ to the complement contribute the amplitude of the
quotient graph $\Gamma/S$ with $S$ collapsed to a single vertex
of valence $\sum_{a \in S} \mathrm{val}(a) - 2(|E_S|)$, where
$|E_S|$ counts edges internal to~$S$. The product of these two
amplitudes is exactly the graph amplitude of the collapsed graph,
as required.
\end{proof}

\begin{theorem}[Cyclic \texorpdfstring{$L_\infty$}{L-infinity} structure via chiral graph
complex; \ClaimStatusProvedHere]\label{thm:cyclic-linf-graph}
\index{cyclic $L_\infty$-algebra!from chiral graph complex}
Let $\cA$ be a Koszul chiral algebra on a smooth projective
curve~$X$ with non-degenerate invariant form
$\langle{-},{-}\rangle_{\cA}$.
The two analytic inputs are now unconditional:
\begin{enumerate}[label=\textup{(H\arabic*)}]
\item\label{hyp:stokes-FM}
 \emph{Stokes regularity on FM compactifications}
 \textup{(}Proposition~\textup{\ref{prop:stokes-regularity-FM}}\textup{)}.
\item\label{hyp:fay-propagator}
 \emph{Fay trisecant identity for the Szeg\H{o} kernel}
 \textup{(}Proposition~\textup{\ref{prop:fay-trisecant}}\textup{)}.
\end{enumerate}
The brackets $\{l_n\}_{n \geq 1}$ of
Construction~\textup{\ref{constr:linf-from-graphs}} equip
$\Defcyc(\cA)$ with the structure of a cyclic $L_\infty$-algebra:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Homotopy Jacobi.}
 For each degree~$N \geq 1$:
 \begin{equation}\label{eq:homotopy-jacobi-graph}
 \sum_{\substack{i + j = N + 1 \\
 \sigma \in \operatorname{Sh}(i,N-i)}}
 \varepsilon(\sigma)\,
 l_j\bigl(l_i(f_{\sigma(1)}, \ldots, f_{\sigma(i)}),\,
 f_{\sigma(i+1)}, \ldots, f_{\sigma(N)}\bigr) \;=\; 0.
 \end{equation}
\item \emph{Recovery.}
 $l_1 = [d_{\barB}, -]$ and
 $l_2 = [-,-]$ coincide with the dg Lie brackets of
 Proposition~\textup{\ref{prop:genus0-cyclic-coderivation}}.
\item \emph{Cyclic symmetry.}
 The pairing~$\eta$ of
 Proposition~\textup{\ref{prop:genus0-cyclic-coderivation}(i)}
 satisfies, for all~$n$:
 \begin{equation}\label{eq:cyclic-symmetry-graph}
 \langle l_n(f_1, \ldots, f_n), f_{n+1}\rangle_\eta
 \;=\;
 (-1)^{n + |f_1|(|f_2|+\cdots+|f_{n+1}|)}
 \langle l_n(f_2, \ldots, f_{n+1}), f_1\rangle_\eta.
 \end{equation}
 In particular, the formal moduli problem
 $\operatorname{MC}(\Defcyc(\cA))$ inherits a $(-1)$-shifted
 symplectic structure.
\end{enumerate}
\end{theorem}

\begin{proof}
(a)\enspace
The homotopy Jacobi identity at degree~$N$ translates into the
vanishing of the sum
$\mathrm{Jac}_N = \sum l_j \circ l_i$
(with appropriate signs and unshuffles).
Express each $l_i$ and $l_j$ as a graph sum. The composition
$l_j \circ l_i$ corresponds to gluing: attach the output of a
tree~$\Gamma_i \in \mathfrak{G}_{i,0}$ to one input of a
tree~$\Gamma_j \in \mathfrak{G}_{j,0}$ to produce a graph
$\Gamma_i \circ_v \Gamma_j$ with exactly one internal edge
joining the two subtrees.

The integral over $\ConfigSpace{k}$ of the
glued graph computes a boundary contribution: the internal edge
carries a propagator $S(z_a, z_b)$ whose pole as
$z_a \to z_b$ localises on a boundary divisor~$D_S$.
By Proposition~\ref{prop:stokes-regularity-FM}(b), the sum of
all boundary contributions equals
$\int_{\ConfigSpace{k}} d\,\omega_N$ for an explicit
form~$\omega_N$. Stokes' theorem yields
$\int d\omega_N = \int_\partial \omega_N$; the boundary strata
are exactly the gluing terms appearing in the Jacobi sum.
By Proposition~\ref{prop:stokes-regularity-FM}(c), each boundary
integral computes the product of graph amplitudes from collapsing
a subset to a vertex. These products correspond bijectively to the
$(l_j \circ l_i)$-terms in $\mathrm{Jac}_N$, and cancel pairwise
by the antisymmetry of~$S$ and the skew-symmetry of the coderivation
bracket.

For the terms where three propagators meet at a common vertex, the
Fay trisecant identity
(Proposition~\ref{prop:fay-trisecant}) ensures the correct
cancellation, replacing the IHX relation of classical graph
homology~\cite{LV12} with its chiral-algebraic analogue on~$X$:
the three graphs related by an IHX move produce amplitudes whose sum
vanishes by~\eqref{eq:algebraic-fay}.

(b)\enspace
At degree $n = 1$: the unique element of $\mathfrak{G}_{1,0}$ is the
single-vertex graph with one external leg and no internal vertices.
Its amplitude is the identity insertion $f_1 \mapsto f_1$, acted on
by the bar differential: $l_1(f_1) = [d_{\barB}, f_1]$.

At degree $n = 2$: $\mathfrak{G}_{2,0}$ contains a single tree, the
edge connecting $v_1$ to~$v_2$, with no internal vertices. Its
amplitude is the commutator $[f_1, f_2]$ of coderivations.

(c)\enspace
Cyclic symmetry. Rotating the inputs $(f_1, \ldots, f_{n+1})$
by one step produces two signs:
\begin{enumerate}
\item \emph{Koszul sign from reordering.} Moving
 $f_1$ (degree $|f_1|$) past
 $f_2 \otimes \cdots \otimes f_{n+1}$
 (total degree $|f_2| + \cdots + |f_{n+1}|$) in the
 graded tensor product gives $(-1)^{|f_1|(|f_2|+\cdots+|f_{n+1}|)}$.
\item \emph{Degree of $l_n$.} The operation $l_n$ has degree
 $2 - n$ (cohomological convention). Moving it past the inner
 product $\langle{-},{-}\rangle_\eta$ (degree~$0$) and
 accounting for the $n$-fold desuspension gives a factor
 $(-1)^n$.
\end{enumerate}
The product of these two factors is exactly the sign
in~\eqref{eq:cyclic-symmetry-graph}. The ribbon structure
on each graph $\Gamma \in \mathfrak{G}_{n,0}$ induces a cyclic
ordering of external legs, and $\mathrm{ad}$-invariance of
$\langle{-},{-}\rangle_\cA$ ensures that the amplitude
$w_\Gamma$ respects the cyclic rotation with this sign.
\end{proof}

\begin{corollary}[Recovery of the Killing cocycle extension;
\ClaimStatusProvedHere]\label{cor:killing-recovery-graph}
\index{Killing cocycle!recovery from graph complex}
By Theorem~\textup{\ref{thm:cyclic-linf-graph}},
for $\widehat{\mathfrak{g}}_k$ with $\mathfrak{g}$ simple and
$k \neq -h^\vee$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item On the generators
 $s^{-1}\bar{\mathfrak{g}} \subset \Defcyc(\widehat{\mathfrak{g}}_k)$:
 $l_3(a,b,c) = \kappa([a,b],c)$, recovering the Killing $3$-cocycle of
 Proposition~\textup{\ref{prop:killing-linf-extension}}.
\item $l_n = 0$ on generators for all $n \geq 4$.
\end{enumerate}
\end{corollary}

\begin{proof}
(i)\enspace
The tree graphs in $\mathfrak{G}_{3,0}$ contributing to $l_3$ on
generators are the tripod graphs: three external legs
meeting at one trivalent internal vertex. (No other tree with
$3$~leaves has all internal valences~$\geq 3$.)
The internal vertex carries the chiral bracket~$m_2$ and the
edges contract via the invariant form, giving
$w_{\text{tripod}}(a,b,c) = \langle [a,b], c \rangle_\kappa
= \kappa([a,b],c)$.
No configuration-space integration is needed (the single internal
vertex contributes a $0$-dimensional moduli space).

(ii)\enspace
Any tree in $\mathfrak{G}_{n,0}$ with $n \geq 4$~leaves
and all internal valences~$\geq 3$ has at least $n - 2 \geq 2$
internal vertices and at least one internal vertex of
valence~$\geq 3$. For
$\cA = \widehat{\mathfrak{g}}_k$, the $A_\infty$ operations
satisfy $m_k = 0$ for $k \geq 3$ on the generators (the OPE is at
most quadratic: $m_1 = 0$, $m_2 = \mu$, $m_k = 0$ for
$k \geq 3$). Every tree with $n \geq 4$ external legs requires
internal vertices with total valence exceeding what $m_2$ alone can
supply, forcing at least one $m_k$ with $k \geq 3$ to appear, which
vanishes.

Alternatively, this follows from
Proposition~\ref{prop:killing-linf-extension}: the degree-$\geq 5$
homotopy Jacobi identities are automatically satisfied by the
truncated system $l_1 = 0$, $l_2 = [-,-]$, $l_3 = \phi$,
$l_n = 0$ for $n \geq 4$, so the graph-complex construction
agrees with this truncation on generators.
\end{proof}

\begin{remark}[Relation to known constructions]
\label{rem:graph-complex-context}
\index{Kontsevich--Soibelman!chiral adaptation}
(i)~On $X = \mathbb{A}^1$, the graph sum reduces to the
Kontsevich--Soibelman $L_\infty$ structure on
$\operatorname{CoDer}(BA)[1]$~\cite{KontsevichSoibelman}.
(ii)~In the Costello--Gwilliam framework~\cite{CG17,CG-vol2}, the
graph sum is perturbative quantization of a holomorphic CS-type
theory on~$X$.
(iii)~The full graph complex
$\bigoplus_L \mathfrak{G}_{n,L}$ carries
Getzler--Kapranov~\cite{GeK98} modular-operadic structure; the
$L > 0$ part encodes the genus tower.
(iv)~Both analytic hypotheses are unconditional:
Proposition~\ref{prop:stokes-regularity-FM} and
Proposition~\ref{prop:fay-trisecant}.
\end{remark}

\begin{remark}[Physical interpretation]\label{rem:graph-complex-physics}
Each chiral graph $\Gamma$ is a tree-level Feynman diagram: external
legs carry deformation inputs, internal edges carry the Szeg\H{o}
propagator $S(z,w)$, and internal vertices carry $A_\infty$
operations. The homotopy Jacobi identity is the Ward identity,
mediated by Stokes' theorem on $\ConfigSpace{k}$. At
$L > 0$ (loop level), $L = g$
loop diagrams produce the genus-$g$ obstruction; the cyclic pairing ensures the BV QME order by
order~\cite{costello-renormalization}.
\end{remark}

\subsection{The modular deformation complex}
\label{subsec:modular-deformation-complex}
\index{modular deformation complex|textbf}

The genus-$0$ cyclic deformation complex
$\Defcyc(\cA)$ (Definition~\ref{def:cyclic-deformation-elementary})
is the tree-level shadow of a modular quantum $L_\infty$-algebra.
The modular version assembles all genera:

\begin{definition}[Modular deformation complex]
\label{def:modular-deformation-complex}
\index{modular deformation complex|textbf}
\index{quantum $L_\infty$ algebra!modular deformation complex}
For a chiral algebra~$\cA$ on a smooth projective curve~$X$, the
\emph{modular deformation complex} is the \emph{quantum
$L_\infty$-algebra} (modular convolution $L_\infty$-algebra)
\begin{equation}\label{eq:modular-deformation-complex}
\operatorname{Def}^{\mathrm{mod}}(\cA)
\;:=\;
\prod_{g,n}
\operatorname{Hom}_{\Sigma_n}\!\bigl(
 C_*(\overline{\mathcal{M}}_{g,n}),\;
 \operatorname{End}_\cA(g,n)
\bigr),
\end{equation}
where:
\begin{itemize}
\item $C_*(\overline{\mathcal{M}}_{g,n})$ denotes chains on the
 Deligne--Mumford compactification, and the product runs over
 stable pairs $(g,n)$ with $2g - 2 + n > 0$;
\item $\operatorname{End}_\cA(g,n)$ is the endomorphism space of
 $\cA^{\otimes n}$ with genus-$g$ curvature;
\item the $L_\infty$ brackets arise from \emph{graph gluing}:
 the binary bracket $\ell_2$ composes endomorphisms along separating
 clutching maps; the BV operator $\ell_1^{(g \geq 1)} = \hbar^g\Delta$
 contracts legs along non-separating clutching maps; the higher
 brackets $\ell_n^{(g)}$ are genus-$g$ stable-graph Feynman amplitudes
 (Theorem~\ref{thm:modular-quantum-linfty}).
\end{itemize}
A Maurer--Cartan element
$\Theta \in
\operatorname{MC}(\operatorname{Def}^{\mathrm{mod}}(\cA))$ is
equivalent to a modular homotopy type on the underlying graded
object of~$\cA$
(Definition~\ref{def:modular-homotopy-abstract}).
The MC equation
$d\Theta + \frac{1}{2}[\Theta,\Theta] = 0$
encodes clutching compatibility at every genus.
\end{definition}

\begin{remark}[Homotopy-invariant deformation complex]
\label{rem:deformation-complex-linfty}
The modular deformation complex of Definition~\ref{def:modular-deformation-complex}
is the strict dg~Lie model of a complete filtered cyclic modular $L_\infty$
algebra $\mathrm{Def}_\infty^{\mathrm{mod}}(\cA)$. The higher brackets
encode homotopy-coherent deformation data: $\ell_3$ governs
obstructions to extending first-order deformations, $\ell_4$ governs
secondary obstructions. The coderivation model computes the
same formal moduli problem \cite{KontsevichSoibelman}.

By Tamarkin's theorem \cite{Tamarkin00}, the deformation complex of a
chiral algebra (viewed as an algebra over the chiral operad, which is a
2-algebra in the sense of $E_n$-operads) carries a canonical $E_2$
structure, a homotopy Gerstenhaber algebra. The bar functor is an
$E_2$-coalgebra functor, not a dg~coalgebra functor; this is the algebraic
source of the bar-cobar adjunction's naturality.

Theorem~H (ChirHoch$^*(\cA)$ polynomial on the Koszul locus) is a
statement about the $L_\infty$ formal moduli problem being smooth:
the obstruction brackets $\ell_{k \geq 3}$ vanish on the Koszul locus,
so the formal moduli space is a polynomial affine space.
\end{remark}

\begin{remark}[Modular versus cyclic]
\label{rem:modular-vs-cyclic-complex}
The restriction of the strict model
$\operatorname{Def}^{\mathrm{mod}}(\cA)$ to genus~$0$
recovers $\Defcyc(\cA)$, and the same is true for the transferred
homotopy object $\Definfmod(\cA)$ after forgetting every
positive-genus Taylor component. At $g \geq 1$, the coefficients are
chains on $\overline{\mathcal{M}}_{g,n}$, so stable-graph geometry
enters the deformation object itself rather than merely its differential
(Remark~\ref{rem:convolution-hierarchy}).
\end{remark}

\begin{construction}[Modular homotopy deformation object]
\label{const:modular-homotopy-deformation-object}
\index{modular deformation!homotopy object|textbf}
Filter $\operatorname{Def}^{\mathrm{mod}}(\cA)$ by genus and
bar length. Choose any complete filtered contraction of this
quantum $L_\infty$-algebra onto a smaller filtered complex.
By the homotopy transfer package of
Appendix~\ref{app:homotopy-transfer}, the transferred higher
brackets $\{\ell_n\}_{n\ge 1}$ endow the target with a cyclic
$L_\infty$-structure. Its filtered $L_\infty$ quasi-isomorphism class
is denoted
\[
\Definfmod(\cA).
\]
The formula in
Definition~\ref{def:modular-deformation-complex} is one explicit
strict chart for this invariant object.
\end{construction}

\begin{proposition}[Strictification principle for modular deformation theory; \ClaimStatusProvedHere]
\label{prop:modular-strictification-principle}
\index{strictification!modular deformation|textbf}
The strict modular deformation complex
$\operatorname{Def}^{\mathrm{mod}}(\cA)$ is a strict model
of $\Definfmod(\cA)$. Consequently:
\begin{enumerate}[label=\textup{(\roman*)}]
\item complete filtered $L_\infty$ quasi-isomorphic choices of strict
 model determine equivalent Maurer--Cartan deformation functors;
\item the genus-zero truncation of
 $\Definfmod(\cA)$ recovers the cyclic
 deformation object $\Defcyc(\cA)$;
\item the canonical class $\Theta_\cA$ is a Maurer--Cartan element whose
 Taylor components simultaneously govern the modular bar differential,
 clutching, and the higher brackets on every transferred model.
\end{enumerate}
\end{proposition}

\begin{proof}
The first statement is exactly the output of homotopy transfer for
complete filtered dg~Lie algebras (Appendix~\ref{app:homotopy-transfer}).
Maurer--Cartan deformation functors are invariant under filtered
$L_\infty$ quasi-isomorphism
\cite{KontsevichSoibelman,Get09}. Restricting the stable-graph
formulas to trees gives genus~$0$. The formulas defining
$D_{\mathrm{tot}}$ and the clutching operators are written as
coderivation actions of $\Theta_\cA$, so the transferred higher
brackets are the same data expressed on a different model.
\end{proof}

\subsection{Concrete modular constructions: from stable graphs to quantum homotopy theory}
\label{subsec:concrete-modular-constructions}
\index{modular homotopy theory!concrete constructions|textbf}
\index{stable graph!bar differential components}

The passage from tree-level to modular homotopy theory
(\S\ref{subsec:tree-to-modular}) replaces rooted trees by stable
graphs. At genus $g \geq 1$, curvature appears:
$\dfib^{\,2} \neq 0$, because propagators circulating around
non-contractible cycles of~$\Sigma_g$ produce period integrals.
The organizing principle: every codimension-$1$ boundary stratum of
$\overline{\mathcal{M}}_{g,n}$ contributes one component of the
modular bar differential; the Maurer--Cartan equation is $\partial^2
= 0$ read through the Feynman transform; and the categorical
logarithm $\barB^{\mathrm{tot}}_X$ of
Remark~\ref{rem:nilpotence-periodicity} acquires its strict
nilpotence $D_{\mathrm{tot}}^2 = 0$ by this mechanism.

\subsubsection{The three-component modular bar differential}
\label{subsubsec:three-component-differential}
\index{modular bar differential!three components|textbf}

Recall from Definition~\ref{def:feynman-transform} that the modular bar
complex is the Feynman transform
$\barB^{\mathrm{mod}}(\cA) = \mathrm{FT}_{\mathcal{M}od}(\cA)$,
with underlying graded space the stable-graph sum
of~\eqref{eq:bar-graph-sum}. Its differential decomposes into three
geometrically distinct components.

\begin{definition}[Three-component modular bar differential]
\label{def:three-component-modular-bar}
\index{modular bar differential!d_int@$d_{\mathrm{int}}$}
\index{modular bar differential!d_sep@$d_{\mathrm{sep}}$}
\index{modular bar differential!d_nonsep@$d_{\mathrm{ns}}$}
Let $\Gamma \in \mathcal{G}^{\mathrm{st}}_{g,n}$ be a stable graph
of genus~$g$ with $n$~legs. On the summand
\[
\barB^{(\Gamma)}(\cA)
\;:=\;
\bigotimes_{v \in V(\Gamma)} \cA(g_v, \operatorname{val}(v))
\;\otimes\; \operatorname{or}(E(\Gamma)),
\]
the modular bar differential is
$d_{\mathrm{mod}} = d_{\mathrm{int}} + d_{\mathrm{sep}} + d_{\mathrm{ns}}$,
where:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Internal differential} $d_{\mathrm{int}}$.
 At each vertex~$v$ of~$\Gamma$ carrying genus label~$g_v$ and
 valence~$\operatorname{val}(v)$, the factor
 $\cA(g_v, \operatorname{val}(v))$ carries its own differential
 $d_v$ built from the $A_\infty$ operations $\{m_k\}$ and the
 genus-$g_v$ propagator on the fiber curve~$\Sigma_{g_v}$.
 The internal differential acts vertex-by-vertex:
 \begin{equation}\label{eq:d-int}
 d_{\mathrm{int}}
 \;=\;
 \sum_{v \in V(\Gamma)}
 \operatorname{id} \otimes \cdots \otimes d_v
 \otimes \cdots \otimes \operatorname{id}.
 \end{equation}
 It preserves the underlying graph~$\Gamma$.

\item \emph{Separating boundary differential} $d_{\mathrm{sep}}$.
 For each edge $e \in E(\Gamma)$ connecting distinct vertices
 $v_1, v_2$ (or each partition of the legs of a single vertex
 creating a separating node), the clutching map
 $\xi_{e}^{\mathrm{sep}}\colon
 \overline{\mathcal{M}}_{g_1, n_1+1} \times
 \overline{\mathcal{M}}_{g_2, n_2+1} \to
 \overline{\mathcal{M}}_{g, n}$
 produces a new graph~$\Gamma/e$ by contracting edge~$e$,
 merging the two endpoint vertices:
 \begin{equation}\label{eq:d-sep}
 d_{\mathrm{sep}} = \sum_{e \in E_{\mathrm{sep}}(\Gamma)}
 \pm\, \iota_e^* \circ \mu_e,
 \end{equation}
 where $\mu_e$ contracts the propagator along edge~$e$ using the
 invariant pairing
 $\langle -, - \rangle_\cA\colon \cA \otimes \cA \to \omega_X$,
 $\iota_e^*$ is the boundary pullback, and the sign is determined
 by the orientation $\operatorname{or}(E(\Gamma))$.
 Geometrically: $d_{\mathrm{sep}}$ implements the separating
 degenerations of the underlying curve.

\item \emph{Non-separating boundary differential} $d_{\mathrm{ns}}$.
 For each loop edge $e$ at vertex~$v$ in~$\Gamma$
 (an edge with both endpoints at~$v$),
 contracting~$e$ produces a graph $\Gamma / e$ in which
 the vertex genus increases by~$1$ ($g_v \mapsto g_v + 1$)
 and the loop disappears ($b_1 \mapsto b_1 - 1$):
 \begin{equation}\label{eq:d-nonsep}
 d_{\mathrm{ns}} = \sum_{\substack{e \in E(\Gamma) \\
 e \text{ loop at } v}}
 \pm\, \mu_e,
 \end{equation}
 where $\mu_e$ contracts the loop edge using the invariant
 pairing $\langle -, - \rangle_\cA$, absorbing the handle
 into the vertex genus. The sign is determined by
 $\operatorname{or}(E(\Gamma))$.
 Geometrically: $d_{\mathrm{ns}}$ contracts non-separating
 nodes, replacing a loop in the dual graph with a handle on
 the curve.
\end{enumerate}
\end{definition}

\begin{proposition}[$d_{\mathrm{mod}}^2 = 0$;
\ClaimStatusProvedHere]\label{prop:d-mod-squared-zero}
\index{modular bar differential!nilpotence}
The modular bar differential satisfies $d_{\mathrm{mod}}^2 = 0$.
\end{proposition}

\begin{proof}
Expand $d_{\mathrm{mod}}^2 = (d_{\mathrm{int}} + d_{\mathrm{sep}}
+ d_{\mathrm{ns}})^2$ into nine terms grouped in three classes.

By Theorem~\ref{thm:prism-higher-genus}(iii),
$d_{\mathrm{mod}}^2 = 0$ follows from the modular operad axioms
(Definition~\ref{def:modular-operad}). We verify this at the
level of the three components.

\emph{Diagonal terms.}
$d_{\mathrm{int}}^2 = 0$: here $d_{\mathrm{int}}$ is the
Feynman-transform internal differential, which acts on
$\barB^{(\Gamma)}(\cA) = \bigotimes_v \cA(g_v,
\operatorname{val}(v)) \otimes \operatorname{or}(E(\Gamma))$
as the total differential on vertex factors: the
\emph{strict} differential $\Dg{g_v}$ at each vertex
(Convention~\ref{conv:higher-genus-differentials}(ii)), which
satisfies $(\Dg{g_v})^2 = 0$ by
Theorem~\ref{thm:quantum-diff-squares-zero}. (The
\emph{fiberwise} curved differential $\dfib$ with
$\dfib^{\,2} = \kappa \cdot \omega_g$ is a separate object,
obtained by restricting to a single fiber.)
$d_{\mathrm{sep}}^2 = 0$ and $d_{\mathrm{ns}}^2 = 0$:
the boundary of a boundary stratum decomposes into
codimension-$2$ strata that cancel in pairs
($\partial^2 = 0$ on $\overline{\mathcal{M}}_{g,n}$).

\emph{Cross terms.}
$d_{\mathrm{int}} d_{\mathrm{sep}} + d_{\mathrm{sep}}
d_{\mathrm{int}} = 0$: edge contraction commutes with the vertex
differential because $d_v$ and the contraction $\mu_e$ act on
disjoint tensor factors (the contracting edge connects two
\emph{different} vertices, and $d_v$ acts on one).
$d_{\mathrm{int}} d_{\mathrm{ns}} + d_{\mathrm{ns}}
d_{\mathrm{int}} = 0$: the self-sewing $\Delta_v$ commutes with
$d_v$ because $\Delta_v$ pairs two marked points via the
$\operatorname{ad}$-invariant form $\langle -,- \rangle_\cA$,
which is a chain map.
$d_{\mathrm{sep}} d_{\mathrm{ns}} + d_{\mathrm{ns}}
d_{\mathrm{sep}} = 0$: codimension-$2$ corner cancellation
in the boundary stratification of $\overline{\mathcal{M}}_{g,n}$.
\end{proof}

\begin{remark}[Genus bookkeeping and exhaustiveness]
\label{rem:genus-bookkeeping}
\index{modular bar differential!genus accounting}
These three components exhaust the codimension-$1$ boundary
contributions to the modular bar differential.
A boundary divisor $D_\Gamma$ of
$\overline{\mathcal{M}}_{g,n}$ is indexed by a stable graph~$\Gamma$ with one edge.
Removing the edge either disconnects~$\Gamma$ (separating,
$d_{\mathrm{sep}}$) or does not (non-separating,
$d_{\mathrm{ns}}$). The third component $d_{\mathrm{int}}$ is
the vertex differential on each
component.

The three components act on the genus decomposition
$g = \sum_v g_v + b_1(\Gamma)$ as follows:
$d_{\mathrm{int}}$ preserves the graph
(hence preserves $b_1$ and all $g_v$);
$d_{\mathrm{sep}}$ contracts an edge between distinct components
(preserving $b_1$ and total genus);
$d_{\mathrm{ns}}$ absorbs a loop edge into a vertex
($g_v \mapsto g_v + 1$, $b_1 \mapsto b_1 - 1$, total
genus preserved).
The total genus $g = \sum_v g_v + b_1(\Gamma)$ is an invariant
of all three.
\end{remark}

\subsubsection{Quantum \texorpdfstring{$L_\infty$}{L-infinity} operations from loop-level graphs}
\label{subsubsec:quantum-linf-from-graphs}
\index{quantum L-infinity algebra@quantum $L_\infty$ algebra!from loop graphs|textbf}

The cyclic $L_\infty$ structure of
Theorem~\ref{thm:cyclic-linf-graph} is built from tree graphs
($L = 0$ loops). The next step extends it to loop-level graphs.
The operations below are written in $A_\infty$ form
(non-symmetric, with ordered inputs); the cyclic pairing
$\langle -, - \rangle_\cA$ symmetrizes them into quantum
$L_\infty$ operations \cite{BL15, Markl06}.

\begin{definition}[Loop-level graph operations]
\label{def:loop-level-graph-ops}
\index{loop-level graph operations}
For $n \geq 0$ and $L \geq 0$, let
$\mathfrak{G}_{n,L}$ be the set of connected graphs with
$n$~external legs, $L$~loops ($b_1 = L$), and vertex genus
labels $\{g_v\}_{v \in V}$ satisfying the stability condition
$2g_v - 2 + \operatorname{val}(v) > 0$ at each vertex.
For each $\Gamma \in \mathfrak{G}_{n,L}$, define the
\emph{loop-level graph amplitude}
\begin{equation}\label{eq:loop-amplitude}
w_\Gamma^{(L)}(f_1, \ldots, f_n)
\;=\;
\int_{\ConfigSpace{|V_{\mathrm{int}}|}(\Sigma)}
\prod_{e \in E_{\mathrm{int}}(\Gamma)} S(z_{s(e)}, z_{t(e)})
\;\cdot\;
\prod_{v \in V(\Gamma)} m_{\mathrm{val}(v)}
\bigl(\text{inputs at } v\bigr),
\end{equation}
where $\Sigma$ is a smooth projective curve,
$V_{\mathrm{int}}$ denotes internal vertices, $S(z,w)$ is
the Szeg\H{o} propagator on~$\Sigma$, and
$m_{\mathrm{val}(v)}$ is the $A_\infty$ vertex operation.

The \emph{genus-$g$ quantum $L_\infty$ operation} is
\begin{equation}\label{eq:quantum-linf-operation}
m_n^{(g)}(f_1, \ldots, f_n)
\;=\;
\sum_{L \geq 0}\;
\sum_{\substack{\Gamma \in \mathfrak{G}_{n,L} \\
 \sum_v g_v + L = g}}
\frac{1}{|\mathrm{Aut}(\Gamma)|}
\, w_\Gamma^{(L)}(f_1, \ldots, f_n).
\end{equation}
The sum runs over all stable graphs whose total genus
$\sum_v g_v + L$ equals~$g$.

For $L \geq 1$, the loop integrals require regularization: the
Szeg\H{o} propagator $S(z,w)$ has a pole along the diagonal, and
loop edges produce $\int S(z,z')\, dz$ with both variables
integrated. Convergence is ensured by the FM compactification
$\overline{C}_n(\Sigma)$, which resolves diagonal singularities
into normal-crossing divisors with logarithmic poles
(Proposition~\ref{prop:stokes-regularity-FM}); the
weight grading on~$\cA$ provides an additional finiteness
bound at each weight.
\end{definition}

\begin{theorem}[Quantum master equation;
\ClaimStatusProvedHere]\label{thm:quantum-master-equation}
\index{quantum master equation!from stable-graph operations}
\index{QME|see{quantum master equation}}
The genus-graded operations $\{m_n^{(g)}\}_{g,n}$ satisfy the
\emph{quantum master equation} (QME): for each $N \geq 0$ and
$G \geq 0$,
\begin{equation}\label{eq:QME}
\sum_{\substack{r + s + t = N \\ g_1 + g_2 = G}}
(-1)^{rs+t}\,
m_{r+1+t}^{(g_1)}\!\bigl(\mathrm{id}^{\otimes r}
\otimes m_s^{(g_2)} \otimes \mathrm{id}^{\otimes t}\bigr)
\;+\;
\sum_{i < j}
(-1)^{\epsilon_{ij}}
m_{N-1}^{(G-1)}\bigl(\Delta_{ij}\bigr)
\;=\; 0,
\end{equation}
where $\Delta_{ij}$ denotes the contraction of inputs $f_i, f_j$
using $\langle -, - \rangle_\cA$ (the self-sewing/non-separating
term), $\epsilon_{ij}$ is the Koszul sign, and the first sum is
the genus-graded $A_\infty$ composition relation (separating term).
\end{theorem}

\begin{proof}
The proof extends the Stokes argument of
Theorem~\ref{thm:cyclic-linf-graph} from trees to graphs with loops.

\emph{Step 1: Two sources of the QME.}
The QME has two structurally distinct contributions,
corresponding to the two types of codimension-$1$ boundary
strata of $\overline{\mathcal{M}}_{g,n}$
(Definition~\ref{def:modular-operad}):

\emph{Separating terms} (first sum in~\eqref{eq:QME}).
For each graph $\Gamma$ contributing at genus~$G$ and degree~$N$,
the graph amplitude integrates a form over
$\ConfigSpace{|V_{\mathrm{int}}|}(\Sigma)$.
Collision of internal vertices produces codimension-$1$ boundary
strata of the configuration space
(Proposition~\ref{prop:stokes-regularity-FM}).
By Stokes' theorem, these boundary contributions give
$m^{(g_1)} \circ m^{(g_2)}$ compositions with $g_1 + g_2 = G$,
exactly as in the tree-level proof of
Theorem~\ref{thm:cyclic-linf-graph}.

\emph{Non-separating terms} (second sum in~\eqref{eq:QME}).
These arise not from the boundary of the configuration space but
from the \emph{graph structure}: contracting a loop edge in
$\Gamma$ (the $d_{\mathrm{ns}}$ component of
Definition~\ref{def:three-component-modular-bar})
pairs two half-edges at a vertex via the invariant form
$\langle -, - \rangle_\cA$, producing the self-sewing contraction
$\Delta_{ij}$ at genus $G - 1$.
Analytically, this corresponds to the period integral
$\oint_\gamma S(z, w)\, dz$ along a homology cycle of $\Sigma$,
which evaluates to a scalar (the period) times the contraction.

\emph{Step 2: $\partial^2 = 0$ on moduli.}
Both contributions are components of the single identity
$d_{\mathrm{mod}}^2 = 0$
(Proposition~\ref{prop:d-mod-squared-zero}),
which is the modular operad boundary relation
$\partial^2 = 0$ on $\overline{\mathcal{M}}_{g,n}$
transported through the Feynman transform.
The separating terms correspond to
$d_{\mathrm{sep}}^2 + d_{\mathrm{int}} d_{\mathrm{sep}}
+ d_{\mathrm{sep}} d_{\mathrm{int}} = 0$;
the non-separating terms to
$d_{\mathrm{ns}}^2 + d_{\mathrm{int}} d_{\mathrm{ns}}
+ d_{\mathrm{ns}} d_{\mathrm{int}} = 0$;
the cross terms to
$d_{\mathrm{sep}} d_{\mathrm{ns}}
+ d_{\mathrm{ns}} d_{\mathrm{sep}} = 0$
(codimension-$2$ corner cancellation).
\end{proof}

\begin{remark}[The unimodularity obstruction]
\label{rem:unimodularity-obstruction}
\index{unimodularity obstruction|textbf}
\index{quantum L-infinity algebra@quantum $L_\infty$ algebra!unimodularity}
The quantum $L_\infty$ structure does not exist for all cyclic
$L_\infty$ algebras. The obstruction to promoting a cyclic
$L_\infty$ algebra to a quantum $L_\infty$ algebra (i.e., adding
the non-separating terms $m_n^{(g)}$ for $g \geq 1$) is the
\emph{unimodularity condition}
\begin{equation}\label{eq:unimodularity}
\Delta(m_0) = 0,
\end{equation}
where $\Delta\colon \operatorname{End}(\cA) \to \mathbb{C}$ is the
BV operator (supertrace of the second-order part).
Concretely: the non-separating self-sewing $\Delta_{ij}$ applied to
the curvature $m_0$ must vanish, or else the genus-$1$ QME has no
solution.

For Koszul chiral algebras, this obstruction is automatically
bypassed:
\begin{enumerate}[label=\textup{(\alph*)}]
\item Central curvature
 (Remark~\ref{rem:voa-central-curvature}):
 $m_0^{(g)} = \kappa(\cA) \cdot \omega_g \cdot \operatorname{id}$
 is a scalar multiple of the identity, hence
 $\Delta(m_0^{(g)}) = \kappa(\cA) \cdot \omega_g
 \cdot \operatorname{str}(\operatorname{id})$.
\item The supertrace is computed weight-by-weight.
 At each conformal weight~$h$, the bar complex
 $\barB_{[h]}$ is finite-dimensional and the Koszul
 reciprocity $h_{\cA}(t) \cdot h_{\cA^!}(-t) = 1$
 \cite[Theorem~3.5.1]{LV12} gives
 $\sum_n (-1)^n \dim \barB^n_{[h]} = 0$ for $h \geq 1$
 (the alternating sum vanishes at each positive weight by
 the functional equation). At weight~$0$,
 $\barB_{[0]} = \mathbb{k}$ contributes
 $\operatorname{str}(\operatorname{id}_{[0]}) = 1$, but
 the curvature $m_0^{(g)}$ has positive weight, so
 $\Delta(m_0^{(g)})_{[h]} = \kappa \cdot \omega_g \cdot
 \operatorname{str}(\operatorname{id}_{[h]}) = 0$
 for all $h$ in the support of~$m_0^{(g)}$.
 Hence $\Delta(m_0^{(g)}) = 0$.
\item Therefore Koszul chiral algebras carry full quantum
 $L_\infty$ structures, and hence full modular homotopy types
 (Definition~\ref{def:modular-homotopy-abstract}), at all genera.
\end{enumerate}
By this mechanism, the universal MC
class~$\Theta_\cA$
(Theorem~\ref{thm:universal-MC}) exists for the Koszul locus.
\end{remark}

\begin{remark}[The QME as $\partial^2 = 0$ on moduli]
\label{rem:qme-boundary-squared}
\index{quantum master equation!geometric origin}
The QME~\eqref{eq:QME} has a single geometric origin:
$\partial^2 = 0$ on chains of $\overline{\mathcal{M}}_{g,n}$.
The two sums correspond to the two types of codimension-$1$
boundary strata:

\smallskip
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lll}
\toprule
\emph{Boundary type} & \emph{Differential component}
 & \emph{QME term} \\
\midrule
Separating node & $d_{\mathrm{sep}}$
 & $\sum m^{(g_1)} \circ m^{(g_2)}$ \\
Non-separating node & $d_{\mathrm{ns}}$
 & $\sum m^{(G-1)}(\Delta_{ij})$ \\
\bottomrule
\end{tabular}
\end{center}
\smallskip

\noindent
The first sum splits the curve into two components of genera
$g_1 + g_2 = G$; the second sum creates a handle, lowering genus by~$1$.
The QME is $\partial^2 = 0$ transported through the Feynman transform.
In physics: the first term is the tree-level factorization of
amplitudes; the second is the BV operator $\Delta$ (the supertrace
over the propagator loop). The entire quantum $L_\infty$ structure
is the shadow of the modular operad axioms on
$\{\overline{\mathcal{M}}_{g,n}\}$.
\end{remark}

\subsubsection{The total differential from
\texorpdfstring{$\Theta_\cA$}{Theta-A}}
\label{subsubsec:total-differential-from-theta}
\index{total differential!from Maurer--Cartan class|textbf}
\index{completed bar complex!total differential}

The universal MC class $\Theta_\cA$ assembles the genus-graded bar
differentials into a single nilpotent on the completed bar
complex.

\begin{theorem}[Total differential from the MC class;
\ClaimStatusProvedHere]\label{thm:total-differential-from-mc}
Let $\cA$ be a modular Koszul chiral algebra for which
$\Theta_\cA \in
\operatorname{MC}(\operatorname{Def}^{\mathrm{mod}}(\cA))$
is constructed
\textup{(}Theorem~\textup{\ref{thm:universal-MC})}.
Define the \emph{total completed bar complex}
\begin{equation}\label{eq:completed-bar-total}
\barB^{\mathrm{tot}}_X(\cA)
\;:=\;
\prod_{g \geq 0} \hbar^{g}\,
\barB_X^{(g)}(\cA)
\end{equation}
with total differential
\begin{equation}\label{eq:D-total-from-theta}
D_{\mathrm{tot}}
\;:=\;
\dzero \;+\; [\Theta_\cA,\, -],
\end{equation}
where $\dzero$ is the genus-$0$ collision differential and
$[\Theta_\cA, -]$ is the coderivation action of $\Theta_\cA$ on
the bar coalgebra, expanded genus-by-genus as
\begin{equation}\label{eq:D-total-expanded}
D_{\mathrm{tot}}\big|_{\barB^{(g)}}
\;=\;
\dzero \;+\;
\sum_{h=1}^{g} \hbar^{h}\,
\bigl[\Theta_\cA^{(h)},\, -\bigr],
\end{equation}
where $\Theta_\cA^{(h)}$ is the genus-$h$ component of the MC
class.
Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $D_{\mathrm{tot}}^2 = 0$ on
 $\barB^{\mathrm{tot}}_X(\cA)$.
\item At fixed genus~$g$, the restriction recovers the
 genus-$g$ total corrected differential:
 $D_{\mathrm{tot}}|_{\barB^{(g)}} = \Dg{g}$
 \textup{(}Convention~\textup{\ref{conv:higher-genus-differentials}(ii))}.
\item The fiberwise curved differential at genus~$g$ is
 $\dfib^{(g)} := D_{\mathrm{tot}}|_{\barB^{(g)}}
 \big|_{[\Sigma_g]}$
 (restriction to the fiber over $[\Sigma_g] \in
 \overline{\mathcal{M}}_g$, with the moduli-variation components
 $d_{\mathrm{sep}}$, $d_{\mathrm{ns}}$ of
 Definition~\textup{\ref{def:three-component-modular-bar}}
 dropped). It satisfies the curvature identity
 $(\dfib^{(g)})^2 = \kappa(\cA) \cdot \omega_g \cdot
 \operatorname{id}$.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Part~(i).}
The MC equation for $\Theta_\cA$ in
$\operatorname{Def}^{\mathrm{mod}}(\cA)$
(Definition~\ref{def:modular-deformation-complex}) states
\begin{equation}\label{eq:mc-for-dtot}
\dzero(\Theta_\cA) + \tfrac{1}{2}[\Theta_\cA, \Theta_\cA] = 0.
\end{equation}
Compute:
\begin{align*}
D_{\mathrm{tot}}^2
&= (\dzero + [\Theta_\cA, -])^2 \\
&= \underbrace{\dzero^2}_{=\,0}
 + \dzero \circ [\Theta_\cA, -]
 + [\Theta_\cA, -] \circ \dzero
 + [\Theta_\cA, [\Theta_\cA, -]] \\
&= [\dzero(\Theta_\cA), -]
 + \tfrac{1}{2}[[\Theta_\cA, \Theta_\cA], -] \\
&= [\dzero(\Theta_\cA) + \tfrac{1}{2}[\Theta_\cA, \Theta_\cA],\, -]
\;=\; 0,
\end{align*}
where the second line uses the graded Jacobi identity for
coderivation brackets, the third line uses the coderivation identity
$\dzero \circ [\Theta, -] + [\Theta, -] \circ \dzero
= [\dzero(\Theta), -]$, and the final step is the
MC equation~\eqref{eq:mc-for-dtot}.

\emph{Part~(ii).}
By construction,
$D_{\mathrm{tot}}|_{\barB^{(g)}} = \dzero +
\sum_{h=1}^g \hbar^h [\Theta^{(h)}, -]$
(equation~\eqref{eq:D-total-expanded}).
The coderivation $[\Theta^{(h)}, -]$ acts on the bar coalgebra
as the genus-$h$ quantum correction to the differential,
which is precisely the period-integral correction $\hbar^h d_h$
of Convention~\ref{conv:higher-genus-differentials}(ii):
the MC class $\Theta^{(h)}$ encodes the same data as the
genus-$h$ propagator correction (by
Theorem~\ref{thm:universal-theta}).
Hence $D_{\mathrm{tot}}|_{\barB^{(g)}} = \Dg{g}$.

\emph{Part~(iii).}
On the fiber over $[\Sigma_g]$, the separating and non-separating
components $d_{\mathrm{sep}}$, $d_{\mathrm{ns}}$ vanish (they
require varying the curve), leaving
$\dfib^{(g)} = d_{\mathrm{int}}|_{[\Sigma_g]}$. Compute:
$(\dfib^{(g)})^2 = (d_{\mathrm{int}})^2|_{[\Sigma_g]}
= \sum_v d_v^2 = \sum_v \kappa(\cA) \cdot \omega_{g_v}$.
For a single-vertex graph ($g_v = g$, the smooth locus of
$\overline{\mathcal{M}}_g$), this gives $\kappa(\cA) \cdot
\omega_g$ directly.
On a multi-vertex graph, $\sum_v \omega_{g_v} = \omega_g$ by
additivity of the Arnold defect across irreducible components
of a nodal curve~\eqref{eq:arnold-defect-hg}.
\end{proof}

\begin{remark}[$D_{\mathrm{tot}}$ as twisted connection; $\Theta_\cA$ as curved twisting cochain]
\label{rem:D-tot-as-connection}%
\label{rem:theta-as-curved-twisting}%
\index{total differential!as twisted connection}
\index{twisting morphism!curved|textbf}
\index{Maurer--Cartan element!as curved twisting cochain}
Formula~\eqref{eq:D-total-from-theta} is a twisted connection:
$\dzero$ is the flat connection on the bar coalgebra,
$\Theta_\cA$ is a gauge field valued in the modular deformation
complex, and $D_{\mathrm{tot}} = \dzero + [\Theta_\cA, -]$ is
the covariant derivative.
The MC equation
$\dzero(\Theta) + \tfrac{1}{2}[\Theta, \Theta] = 0$
is the flatness condition $D_{\mathrm{tot}}^2 = 0$.

This has a precise formulation in the language of twisting cochains
(Remark~\ref{rem:theta-modular-twisting}):
the genus-$0$ canonical twisting morphism $\tau_0$ extends to a
\emph{modular twisting cochain}
$\tau_{\mathrm{mod}} = \tau_0 + \Theta_\cA$
in the modular convolution algebra, whose genus-$g$ curvature
$\kappa(\cA)\cdot\omega_g$ is the Arnold defect.
The cyclic $L_\infty$ operations $\{l_n\}$ on
$H^*_{\mathrm{cyc}}(\cA,\cA)$ are the Taylor coefficients of the
coderivation $[\Theta_\cA, -]$: the $L_\infty$ structure \emph{is}
the twisting cochain, read as an algebra structure on the
deformation complex.
\end{remark}

\begin{remark}[Clutching compatibility of $D_{\mathrm{tot}}$]
\label{rem:clutching-D-tot}
\index{clutching compatibility!total differential}
Since $\Theta_\cA$ is an MC element in the modular convolution
algebra $\widehat{L}_{\Gmod}$
(Proposition~\ref{prop:geometric-modular-operadic-mc}),
it satisfies clutching
compatibility~\eqref{eq:clutching-factorization}:
\[
\xi_{\mathrm{sep}}^*(\Theta^{(g)})
= \sum_{g_1+g_2=g} \Theta^{(g_1)} \star \Theta^{(g_2)},
\qquad
\xi_{\mathrm{ns}}^*(\Theta^{(g+1)})
= \Delta_{\mathrm{ns}}(\Theta^{(g)}).
\]
This means the total differential $D_{\mathrm{tot}}$ is
compatible with the modular operad structure: restricting to a
boundary stratum (separating or non-separating degeneration) gives
the tensor product (resp.\ self-sewing) of the differentials on the
two (resp.\ one) irreducible component(s). Equivalently,
$D_{\mathrm{tot}}$ is a \emph{modular bar differential} in the
sense of Definition~\ref{def:three-component-modular-bar}:
$D_{\mathrm{tot}} = d_{\mathrm{int}} + d_{\mathrm{sep}} +
d_{\mathrm{ns}}$ with the three components induced by~$\Theta_\cA$.
\end{remark}

\subsubsection{Virtual bar family and characteristic hierarchy}
\label{subsubsec:virtual-bar-k-class}
\index{virtual bar family|textbf}
\index{K-theory@$K$-theory!virtual bar class}

\begin{definition}[Virtual bar $K$-class]
\label{def:virtual-bar-k-class}
For a modular Koszul chiral algebra $\cA$, the
\emph{virtual bar family at genus~$g$} is the derived pushforward
\begin{equation}\label{eq:virtual-bar-k-class}
\mathbf{V}_{\cA}^{(g)}
\;:=\;
R\pi_{g*}\, \barB^{(g)}_X(\cA)
\;\in\; D^b(\overline{\mathcal{M}}_g),
\end{equation}
where $\pi_g\colon \overline{\mathcal{C}}_g \to
\overline{\mathcal{M}}_g$ is the universal curve. Its class in
$K$-theory is the \emph{virtual bar $K$-class}
\begin{equation}\label{eq:V-A-K-class}
V_{\cA}
\;:=\;
[R\pi_{g*}\, \barB^{(g)}_X(\cA)]
\;\in\; K^0(\overline{\mathcal{M}}_g).
\end{equation}
\end{definition}

\begin{proposition}[Characteristic hierarchy;
\ClaimStatusProvedHere]\label{prop:characteristic-hierarchy}
\index{characteristic hierarchy|textbf}
\index{modular characteristic package!K-theoretic}
The virtual bar $K$-class $V_\cA$ determines a three-level
hierarchy of invariants:
\begin{enumerate}[label=\textup{(L\arabic*)}]
\item \emph{Scalar level.}
 The first Chern class of the determinant line bundle recovers the
 scalar modular characteristic:
 \[
 c_1(\det V_\cA)
 \;=\;
 \kappa(\cA) \cdot \lambda
 \;\in\; \operatorname{Pic}(\overline{\mathcal{M}}_g),
 \]
 where $\lambda = c_1(\det \mathbb{E}^\vee)$ is the Hodge class.
 This is Theorem~\textup{\ref{thm:modular-characteristic}}:
 $\kappa(\cA)$ is the scalar modular characteristic.

\item \emph{Spectral level.}
 The Chern character of $V_\cA$ determines the spectral
 discriminant:
 \[
 \Delta_\cA(x)
 \;=\;
 \det(1 - x \cdot T_{\mathrm{rec}})
 \;=\;
 \prod_i (1 - \lambda_i x),
 \]
 where the $\lambda_i$ are the Chern roots of $V_\cA$
 and $T_{\mathrm{rec}}$ is the recursion operator
 \textup{(}Theorem~\textup{\ref{thm:discriminant-spectral})}.
 This encodes the full bar cohomology dimensions at all weights.

\item \emph{Holonomy level.}
 The flat connection on $V_\cA$ (from the Gauss--Manin connection
 on $R\pi_{g*}$) determines the periodicity profile
 \[
 \Pi_\cA \;=\; (M_\cA,\, Q_\cA,\, G_\cA)
 \;\;:\;\;
 \text{monodromy, quasiperiod, Galois data}
 \]
 \textup{(}Remark~\textup{\ref{rem:periodicity-triple})}.
 For rational central charge, the monodromy group
 $M_\cA \leq \mathrm{GL}(V_\cA)$ has finite image
 (the $T$-matrix has finite order on the character space).
\end{enumerate}
The three levels correspond to $\det$, $\mathrm{ch}$, and
$\mathrm{Hol}$ respectively: the standard filtration of
information in a $K$-class with connection.
\end{proposition}

\begin{proof}
\emph{(L1)}\enspace
By Grothendieck--Riemann--Roch on the universal curve
$\pi_g\colon \overline{\mathcal{C}}_g \to \overline{\mathcal{M}}_g$
(\S\ref{subsec:why-ahat}):
\[
c_1(\det R\pi_{g*} \barB^{(g)})
\;=\;
\pi_{g*}\!\bigl(\mathrm{ch}_1(\barB|_{\mathrm{fiber}})
\cdot \mathrm{Td}(T_\pi)\bigr).
\]
The fiber Chern character $\mathrm{ch}_1(\barB|_{\Sigma_g})
= \kappa(\cA)$ (Theorem~\ref{thm:modular-characteristic}),
and $\pi_{g*}(\mathrm{Td}_1(T_\pi)) = \lambda$
(Mumford's formula \cite{Mumford83}).
Hence $c_1(\det V_\cA) = \kappa(\cA) \cdot \lambda$.

\emph{(L2)}\enspace
The full Chern character $\mathrm{ch}(V_\cA)$
encodes the dimensions $\dim H^n(\barB^{(g)}_{[h]})$ at each
weight~$h$ and bar degree~$n$, which are the coefficients of the
spectral discriminant generating function
(Theorem~\ref{thm:ds-bar-gf-discriminant}).

\emph{(L3)}\enspace
The Gauss--Manin connection on
$\barB^{(g)}_X(\cA) \to \overline{\mathcal{M}}_g$
is flat (its curvature is the Kodaira--Spencer class, which acts
nilpotently on cohomology by
Theorem~\ref{thm:kodaira-spencer-chiral-complete}).
The monodromy representation records the action
of $\pi_1(\mathcal{M}_g) = \mathrm{MCG}(\Sigma_g)$ on the bar
cohomology fibers.
\end{proof}

\begin{remark}[Three readings of the virtual bar class]
\label{rem:three-readings-V}
\index{virtual bar family!three readings}
The hierarchy (L1)--(L3) reflects the three standard ways of
extracting invariants from a $K$-class: Euler characteristic,
Chern character, holonomy. In the categorical logarithm paradigm:
\begin{itemize}
\item \emph{(L1)} $\det V_\cA = \kappa \cdot \lambda$
 is the \emph{leading coefficient} of the logarithm
 (Theorem~D$_{\mathrm{scal}}$).
\item \emph{(L2)} $\mathrm{ch}(V_\cA) \leftrightarrow \Delta_\cA(x)$
 is the \emph{Taylor expansion} of the logarithm
 (Theorem~D$_\Delta$).
\item \emph{(L3)} $\mathrm{Hol}(V_\cA) = \Pi_\cA$
 is the \emph{monodromy} of the logarithm, the ambiguity in
 choosing a branch (the periodicity profile).
\end{itemize}
This realizes the passage
$\kappa \to \Delta \to \Pi$
(\emph{scalar $\to$ spectral $\to$ holonomy}) as the natural
filtration of information in the $K$-class $V_\cA$, just as the
passage $c_1 \to \mathrm{ch} \to \nabla$ is the natural filtration
of information in a vector bundle with connection. The Heisenberg
specialization
(Chapter~\ref{ch:heisenberg-frame},
 Definition~\ref{def:frame-modular-package})
illustrates all three levels: $\kappa = k$ (the level),
$\Delta = 1/(1-x)$ (free boson),
$\Pi = (\mathbb{Z}, k\mathbb{Z}, \{1\})$ (abelian periodicity).
The precise minimal periodicity of the bar cohomology dimensions is
still open; the proved hierarchy records only the finite-image
monodromy consequence at rational central charge.
\end{remark}

\subsubsection{Chiral homology from the modular bar complex}
\label{subsubsec:chiral-homology-recovery}
\index{chiral homology!from modular bar complex|textbf}

\begin{theorem}[Chiral homology recovery;
\ClaimStatusProvedHere]\label{thm:chiral-homology-recovery}
\index{chiral homology!bar complex identification}
Let $\cA$ be a modular Koszul chiral algebra on a smooth projective
curve $X$ of genus~$g$. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Fiberwise identification.}
 The chiral homology of~$\cA$ on the fixed curve $\Sigma_g$ is
 computed by the bar complex:
 \begin{equation}\label{eq:chiral-homology-bar}
 H^{\mathrm{ch}}_n(\Sigma_g, \cA)
 \;\cong\;
 H^n\bigl(\barB^{(g)}_X(\cA)\big|_{[\Sigma_g]},\;
 \Dg{g}\big|_{[\Sigma_g]}\bigr)
 \end{equation}
 for all $n \geq 0$, where $\Dg{g}\big|_{[\Sigma_g]}$ is the
 square-zero flat comparison differential at
 $[\Sigma_g] \in \overline{\mathcal{M}}_g$. When
 $\kappa(\cA) \neq 0$, the curved fiber operator $\dfib^{(\Sigma_g)}$
 is interpreted only coderivedly.

\item \emph{Center sheaf.}
 The local system on $\overline{\mathcal{M}}_g$ whose fiber
 over $[\Sigma_g]$ is $H^{\mathrm{ch}}_*(\Sigma_g, \cA)$ is the
 center sheaf:
 \begin{equation}\label{eq:center-sheaf-bar}
 \mathcal{Z}_\cA
 \;=\;
 R^*\!\pi_{g*}\,
 \bigl(\barB^{(g)}_X(\cA),\, \Dg{g}\bigr)
 \;\in\;
 \operatorname{Loc}(\overline{\mathcal{M}}_g).
 \end{equation}

\item \emph{Global sections.}
 The ambient complementarity complex
 \textup{(}Theorem~\textup{\ref{thm:quantum-complementarity-main})}
 is recovered as
 \begin{equation}\label{eq:ambient-from-bar}
 C_g(\cA) \;=\; R\Gamma(\overline{\mathcal{M}}_g,\,
 \mathcal{Z}_\cA)
 \;\cong\;
 H^*\bigl(\barB^{(g)}_X(\cA),\, D_{\mathrm{tot}}\bigr),
 \end{equation}
 and the Verdier involution $\sigma$ on $C_g(\cA)$ arises from
 Verdier duality $\mathbb{D}_{\operatorname{Ran}}$ on the bar
 coalgebra
 \textup{(}Theorem~\textup{\ref{thm:higher-genus-inversion})}.

\item \emph{Genus tower.}
 The full genus tower of chiral homology is assembled by the
 completed bar complex:
 \begin{equation}\label{eq:chiral-homology-tower}
 \bigoplus_{g \geq 0} \hbar^{g}\,
 H^{\mathrm{ch}}_*(\Sigma_g, \cA)
 \;\cong\;
 H^*\bigl(\barB^{\mathrm{tot}}_X(\cA),\, D_{\mathrm{tot}}\bigr),
 \end{equation}
 with the genus filtration corresponding to the $\hbar$-adic
 filtration on the completed bar.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Part~(i).}
On a fixed curve $\Sigma_g$, the chiral homology
$H^{\mathrm{ch}}_*(\Sigma_g, \cA)$ is by definition
\cite[3.4.4]{BD04} the derived pushforward of $\cA^{\boxtimes n}$
along the Ran space $\operatorname{Ran}(\Sigma_g)$. The bar
construction computes this pushforward
(Theorem~\ref{thm:geometric-equals-operadic-bar} for genus~$0$;
Theorem~\ref{thm:prism-higher-genus} for the extension to all
genera via the Feynman transform): the bar complex on
$\overline{C}_n(\Sigma_g)$ with the flat comparison differential
$\Dg{g}\big|_{[\Sigma_g]}$ computes the same ordinary cohomology as
the Ran-space pushforward. If $\kappa(\cA) \neq 0$, the raw fiberwise
operator $\dfib^{(\Sigma_g)}$ is curved and therefore belongs on the
coderived side rather than in ordinary cohomology.

\emph{Part~(ii).}
The assignment $[\Sigma_g] \mapsto
H^{\mathrm{ch}}_*(\Sigma_g, \cA)$ varies in a local system because
the flat comparison bar complex is a square-zero family over
$\overline{\mathcal{M}}_g$
(the bar family of~\eqref{eq:bar-family}), and the formation of
cohomology of a flat family produces a local system. The resulting
local system is precisely the center sheaf $\mathcal{Z}_\cA$ of
Beilinson--Drinfeld~\cite[3.4.10]{BD04}.

\emph{Part~(iii).}
Global sections of $\mathcal{Z}_\cA$ over
$\overline{\mathcal{M}}_g$ compute
$R\Gamma(\overline{\mathcal{M}}_g, \mathcal{Z}_\cA)$
by definition.
By the Leray spectral sequence for
$\pi_g\colon \overline{\mathcal{C}}_g \to \overline{\mathcal{M}}_g$,
this agrees with
$H^*(\barB^{(g)}_X(\cA), D_{\mathrm{tot}})$ when the total
differential is used (incorporating both the fiberwise part and
the moduli variation). The Verdier involution on $C_g(\cA)$
arises from the Verdier duality
$\mathbb{D}_{\operatorname{Ran}} \barB_X(\cA) \simeq
\barB_X(\cA^!)$
(Theorem~\ref{thm:higher-genus-inversion}), which exchanges
$\cA$ and~$\cA^!$ on the bar level and induces $\sigma$ on
global sections.

\emph{Part~(iv).}
The genus-completed product~\eqref{eq:completed-bar-total} is
an inverse limit $\barB^{\mathrm{tot}} = \varprojlim_g
\bigoplus_{h \leq g} \hbar^h \barB^{(h)}$. Each finite
truncation has well-defined cohomology by parts~(i)--(iii).
The transition maps are surjective on cohomology (the genus
filtration is separated and complete by
Proposition~\ref{prop:geometric-modular-operadic-mc}(a)),
so the Mittag-Leffler condition is satisfied and
$H^*(\barB^{\mathrm{tot}}, D_{\mathrm{tot}})
\cong \varprojlim_g H^*(\bigoplus_{h \leq g}
\barB^{(h)}, D_{\mathrm{tot}})$
by \cite[Proposition~3.5.7]{Weibel94}.
Theorem~\ref{thm:total-differential-from-mc}(i) gives
$D_{\mathrm{tot}}^2 = 0$.
\end{proof}

\begin{remark}[The full recovery diagram]
\label{rem:full-recovery-diagram}
\index{modular homotopy theory!recovery diagram}
The constructions of this subsection fit into a single commutative
diagram:
\[
\begin{tikzcd}[column sep=large, row sep=large]
\text{Quantum } L_\infty
 \arrow[r, "\text{MC}"]
 \arrow[d, "g{=}0"']
& \Theta_\cA \in
 \operatorname{MC}(\operatorname{Def}^{\mathrm{mod}})
 \arrow[r, "\text{twist}"]
 \arrow[d, "\text{clutch}"]
& (\barB^{\mathrm{tot}},\, D_{\mathrm{tot}})
 \arrow[d, "R\pi_{g*}"]
\\
\text{Cyclic } L_\infty
 \arrow[r, "\text{Kill.}"]
& \xi^*(\Theta^{(g)})
& \mathcal{Z}_\cA
 \arrow[r, "R\Gamma"]
& C_g = Q_g \oplus Q_g^!
\end{tikzcd}
\]

\noindent
Three paths through this diagram recover three aspects of the
modular homotopy type:

\smallskip
\emph{Top row} (``algebraic path''): the quantum $L_\infty$
operations, packaged as the MC element $\Theta_\cA$, twist the
genus-$0$ bar differential to produce $D_{\mathrm{tot}}$. This is
the bar-coalgebra route: the modular homotopy type is the
\emph{totalization} of the genus tower.

\smallskip
\emph{Right column} (``geometric path''): the total bar complex
pushes forward along the universal curve to produce the center
sheaf $\mathcal{Z}_\cA$; its global sections are the
complementarity complex $C_g(\cA) = Q_g \oplus Q_g^!$. This
is the sheaf-on-moduli route: the modular homotopy type is the
\emph{variation} of the bar complex over
$\overline{\mathcal{M}}_g$.

\smallskip
\emph{Bottom row} (``clutching path''): the genus-$0$ cyclic
$L_\infty$ produces the tree-level structure; the clutching
maps $\xi_{\mathrm{sep}}^*$, $\xi_{\mathrm{ns}}^*$ reconstruct
the full center sheaf from its boundary behavior: the
Getzler--Kapranov route, where the modular homotopy type is the
\emph{modular operad structure} on the collection
$\{H^{\mathrm{ch}}_*(\Sigma_g, \cA)\}$.

\smallskip\noindent
All three paths commute. The single geometric fact underlying all of
them is $\partial^2 = 0$ on $\overline{\mathcal{M}}_{g,n}$, read
through the Feynman transform.
\end{remark}

\subsection{Non-scalar universal classes}
\label{subsec:non-scalar-theta}
\index{Theta_A@$\Theta_\cA$!non-scalar|textbf}

Corollary~\ref{cor:scalar-saturation} gives only one-channel
line concentration in general:
\[
\Theta_\cA^{\min} = \eta \otimes \Gamma_{\cA}
\qquad\text{whenever } \dim H^2_{\mathrm{cyc}}(\cA,\cA) = 1.
\]
On the proved scalar lane this further specializes to
\[
\Theta_\cA^{\min} = \kappa(\cA) \cdot \eta \otimes \Lambda
\qquad\text{with } \Gamma_{\cA}=\kappa(\cA)\Lambda.
\]
We construct the universal non-scalar class
for algebras with
$\dim H^2_{\mathrm{cyc}}(\cA,\cA) \geq 2$.

\begin{construction}[HPT non-scalar MC recursion]
\label{constr:non-scalar-hpt}
\index{homotopy perturbation theory!non-scalar MC}
Let $L = \Defcyc(\cA)$ be the cyclic deformation complex
with homotopy transfer data $(i,p,h,\ell_n)$ from a
minimal model. Choose a basis
$\eta_1, \ldots, \eta_r \in H^2_{\mathrm{cyc}}(\cA,\cA)$
and modular coefficients $U_1, \ldots, U_r \in \mathfrak{m}_{R}$
(the maximal ideal of the modular deformation ring).
The universal non-scalar MC element is built recursively:
\begin{equation}\label{eq:hpt-nonscalar-recursion}
\Theta^{(1)} = i\!\Bigl(\sum_{i=1}^r \eta_i \otimes U_i\Bigr),
\qquad
\Theta^{(N)} = -h\!\Biggl(
 \sum_{n \geq 2} \frac{1}{n!}
 \sum_{\substack{N_1 + \cdots + N_n = N \\ N_j \geq 1}}
 \ell_n\bigl(\Theta^{(N_1)}, \ldots, \Theta^{(N_n)}\bigr)
\Biggr).
\end{equation}
The obstruction equations cut out the modular deformation locus:
\[
p\!\Biggl(
 \sum_{n \geq 2} \frac{1}{n!}\,
 \ell_n(\Theta, \ldots, \Theta)
\Biggr) = 0.
\]
\end{construction}

\begin{example}[Two-channel explicit formula]
\label{ex:two-channel-nonscalar}
\index{Theta_A@$\Theta_\cA$!two-channel formula}
For $r = 2$, with basis $\eta_1, \eta_2$, the first
terms of the non-scalar universal class are:
\begin{equation}\label{eq:two-channel-explicit}
\begin{split}
\Theta_\cA^{\mathrm{ns}}
&= \eta_1 \otimes U_1
 + \eta_2 \otimes U_2
 - \tfrac{1}{2}\,h\ell_2(\eta_1,\eta_2)
 \otimes U_1 U_2 \\
&\quad - \tfrac{1}{6}\,h\ell_3(\eta_1,\eta_1,\eta_2)
 \otimes U_1^2 U_2
 - \tfrac{1}{6}\,h\ell_3(\eta_1,\eta_2,\eta_2)
 \otimes U_1 U_2^2
 + O(4).
\end{split}
\end{equation}
The class is genuinely non-scalar if and only if some mixed
coefficient $U_i U_j$ survives in gauge-normal form.
\end{example}

\begin{proposition}[Non-scalar criterion;
\ClaimStatusProvedHere]
\label{prop:non-scalar-criterion}
\index{Theta_A@$\Theta_\cA$!non-scalar criterion}
The universal class $\Theta_\cA$ is genuinely non-scalar
if and only if, in minimal cyclic model form, some mixed
transferred bracket
$\ell_n(\eta_{i_1}, \ldots, \eta_{i_n})$ with at least two
distinct basis indices produces a homotopy correction not
removable by gauge transformation.
Equivalently: after reduction to gauge-normal form,
some mixed monomial
$U_{i_1} \cdots U_{i_k}$ with $|\{i_1, \ldots, i_k\}| \geq 2$
has nonzero coefficient.
\end{proposition}

\begin{proof}
The gauge group acts by
$\Theta \mapsto e^{g} \cdot \Theta :=
\sum_{n=0}^\infty \frac{1}{n!}\, \ell_n(g, \ldots, g, \Theta)$
for $g \in L^1$. In gauge-normal form
$\operatorname{Im}(h) \cap \operatorname{Im}(\Theta) = 0$,
the recursion~\eqref{eq:hpt-nonscalar-recursion} has no
further gauge freedom. A non-scalar monomial $U_i U_j$
in~$\Theta^{(2)}$ arises from
$h\ell_2(\eta_i, \eta_j) \neq 0$ in the homotopy-transfer
data. Since $h$ is a homotopy (not a chain map), this
correction is algebraically independent of the scalar terms.
\end{proof}

\begin{remark}[Non-scalar landscape]
\label{rem:non-scalar-landscape}
\index{Theta_A@$\Theta_\cA$!non-scalar landscape}
All accessible families considered here (Kac--Moody at generic
level, Virasoro, principal $\mathcal{W}_N$) have
$\dim H^2_{\mathrm{cyc}}(\cA,\cA) = 1$, so their minimal
Maurer--Cartan class lies on a single cyclic line. On the proved
uniform-weight scalar lane this line is
$\kappa(\cA)\Lambda$; for principal $\mathcal{W}_N$ with $N\geq 3$
that stronger identification remains open. Non-scalar
$\Theta_\cA$ requires $\dim H^2_{\mathrm{cyc}} \geq 2$; candidates
include admissible-level Kac--Moody, products, and extended
algebras.
\end{remark}

\section{Stratified periodicity framework}

\subsection{Overview: three sources of periodicity}

The Hochschild cohomology of chiral algebras can exhibit three types of periodicity: \emph{Type I (Modular)}, from rational central charge and modular transformations; \emph{Type II (Quantum)}, from quantum groups at roots of unity; and \emph{Type III (Geometric)}, from the topology of the underlying curve.

\begin{remark}\label{rem:periodicity-scope}
The unconditional core is the quantum periodicity input and the
structural theorem that independent periodicity sources combine by lcm.
Explicit modular periods, sharp geometric periods, and higher-rank
closed formulas are conjectural outside the rank-$1$/minimal-model test
cases.
\end{remark}

\subsection{Type I: modular periodicity from rational central charge}

\subsubsection{The mechanism}

\begin{remark}[Periodicity as exponential of the scalar characteristic]
\label{rem:periodicity-as-exponential}
\index{nilpotence-periodicity correspondence!Type I application}
The scalar characteristic $\kappa(\cA)$ is the infinitesimal datum; the modular period $N$ is the exponential datum (Remark~\ref{rem:nilpotence-periodicity}). For $c = p'/q'$, the $T$-matrix eigenvalues $\lambda_{r,s} = \exp(2\pi i(h_{r,s} - c/24))$ have period $N = 24q'/\gcd(p',24)$, the smallest $N$ with $Nc/24 \in \mathbb{Z}$. The periodicity profile $\Pi(\cA) = (M_\cA, Q_\cA, G_\cA)$ (Remark~\ref{rem:periodicity-triple}) is the exponential package of the logarithmic package $(\kappa(\cA), \Delta_\cA, \Theta_\cA)$.
\end{remark}

\begin{conjecture}[Modular periodicity for minimal models; \ClaimStatusConjectured]
\label{conj:modular-periodicity-minimal}
\index{periodicity!modular!minimal models|textbf}
Let $M(p,q)$ be a Virasoro minimal model with $2 \leq p < q$, $\gcd(p,q) = 1$,
and central charge $c = 1 - 6(p-q)^2/(pq)$. Write $c = p'/q'$ in lowest terms
and set
\[
N \;=\; \frac{24q'}{\gcd(p',24)}.
\]
Then for all bar degrees $n$ and all sufficiently large conformal weight $h$:
\[
\dim H^n(\bar{B}_{[h+N]}^{\mathrm{ch}}(M(p,q)))
\;=\;
\dim H^n(\bar{B}_{[h]}^{\mathrm{ch}}(M(p,q))).
\]
(Part of the MC2 theorem package; Theorem~\ref{thm:mc2-full-resolution}.)
\end{conjecture}

\begin{evidence}
The following three-step argument establishes the structural
framework; however, Step~2 contains a gap in the passage from
theta-function periodicity to weight-space dimension periodicity
(the convolution with $1/\eta$ does not preserve eventual
periodicity of Fourier coefficients, confirmed computationally
in Computation~\ref{comp:m58-weight-space-periodicity}).
Step~1 ($T$-matrix periodicity) is unconditional.

\smallskip\noindent
The argument proceeds in three steps: we establish $T$-matrix periodicity, deduce
periodicity of the module decomposition data, and lift to the bar complex.

\emph{Step~1: $T$-matrix periodicity.}
The minimal model $M(p,q)$ has exactly $(p-1)(q-1)/2$ irreducible modules
$V_{r,s}$ with $1 \leq r \leq p-1$, $1 \leq s \leq q-1$, subject to the
identification $V_{r,s} = V_{p-r,q-s}$. Their conformal weights are
\[
h_{r,s} \;=\; \frac{(qr - ps)^2 - (q-p)^2}{4pq}.
\]
The $T$-matrix is diagonal: $T_{(r,s),(r',s')} = \delta_{(r,s),(r',s')}
\, e^{2\pi i(h_{r,s} - c/24)}$. Write
\[
\lambda_{r,s} := e^{2\pi i(h_{r,s} - c/24)}.
\]
Then $\lambda_{r,s}^N = 1$ is equivalent to
$N(h_{r,s} - c/24) \in \mathbb{Z}$. Since $h_{r,s} - c/24$ is rational
with denominator dividing $24pq$ and
$N = 24q'/\gcd(p',24)$, one gets $T^N = \mathrm{Id}$ on the
finite-dimensional character space:

$\tau \mapsto \tau + 1$ multiplies the character by the phase
$e^{-2\pi i c/24}$, while
\[
\frac{cN}{24} = \frac{p'N}{24q'} = \frac{p'}{\gcd(p',24)} \in \mathbb{Z},
\]
because $\gcd(p',24)$ divides $p'$.

\emph{Step~2: Periodicity of weight-space dimensions.}
The character of each irreducible module $V_{r,s}$ is given by the
Rocha-Caridi formula:
\[
\mathrm{ch}_{V_{r,s}}(\tau) \;=\; \frac{\Theta_{r,s}(\tau)}{\eta(\tau)}
\]
where $\Theta_{r,s} = \theta_{qr-ps,\,2pq} - \theta_{qr+ps,\,2pq}$ is a
difference of level-$2pq$ theta functions and $\eta$ is the Dedekind eta
function. The Fourier coefficients of the level-$\ell$ theta function
$\theta_{m,\ell}(\tau) = \sum_{n \in \mathbb{Z}} q^{(m + 2\ell n)^2/(4\ell)}$
are supported on the arithmetic progression $\{(m + 2\ell n)^2/(4\ell) : n \in \mathbb{Z}\}$
and are periodic in the exponent variable with period~$\ell$.

Now $\dim V_{r,s,\,[k]}$ is the coefficient of $q^{h_{r,s} + k - c/24}$ in
$\mathrm{ch}_{V_{r,s}}$. This coefficient equals the convolution of the
theta-function coefficients with the partition function $p(\cdot)$
(from $1/\eta$). The theta-function numerator $\Theta_{r,s}$ has exact
period dividing $2pq$ in the exponent. Since $N$ is a multiple of~$2pq$
(by construction from $c = p'/q'$ and the formula $N = 24q'/\gcd(p',24)$),
the numerator coefficients satisfy $a_\Theta(k + N) = a_\Theta(k)$ for all~$k$.

For the convolution: writing $\dim V_{r,s,\,[k]} = \sum_{j \geq 0} a_\Theta(k-j)\, p(j)$
where $a_\Theta$ denotes the theta-function coefficients and $p(j)$ the
partition function, the $N$-periodicity of~$a_\Theta$ gives
\[
\dim V_{r,s,\,[k+N]} - \dim V_{r,s,\,[k]}
\;=\; \sum_{j > k} \bigl(a_\Theta(k + N - j) - a_\Theta(k - j)\bigr)\, p(j)
\]
which vanishes for $k$ sufficiently large (specifically, for $k$ exceeding
the maximal pole order of $\Theta_{r,s}/\eta$, the sum on the right is empty).
Hence $\dim V_{r,s,\,[k+N]} = \dim V_{r,s,\,[k]}$ for all $k \gg 0$.

\begin{remark}[Step~2 gap: stabilization threshold]
\label{rem:step2-stabilization-threshold}
The convolution $\dim V_{r,s,[k]} = \sum_j a_\Theta(k-j)\, p(j)$ does not preserve eventual periodicity because $p(j)$ grows sub-exponentially.

\begin{computation}[M(5,8) weight-space dimensions; \ClaimStatusProvedHere]
\label{comp:m58-weight-space-periodicity}
For $M(5,8)$ ($c = -7/20$, $14$ modules, $N = 480$), the Rocha-Caridi formula
$\dim V_{r,s,[k]} = \sum_{n \in \mathbb{Z}} [p(k - \delta^+_n) - p(k - \delta^-_n)]$
(where $\delta^\pm_n$ are the standard null-vector exponents)
gives monotonically increasing sequences for all $14$ modules through $k = 80$. No eventual periodicity is detected at any period dividing $N = 480$ or $pq = 40$.
\end{computation}

Bar \emph{cohomology} periodicity may still hold via the bar differential, but this requires computing OPE structure constants of $M(5,8)$.
\end{remark}

\emph{Step~3: Lift to bar complex.}
The bar complex $\bar{B}^{(n)}_{[h]}(M(p,q))$ in degree~$n$ at conformal
weight~$h$ has dimension given by a finite sum over module labels weighted
by fusion multiplicities:
\[
\dim \bar{B}^{(n)}_{[h]} \;=\; \sum_{\substack{(r_1,s_1),\ldots,(r_n,s_n) \\
k_1 + \cdots + k_n = h - \sum_j h_{r_j,s_j}}}
\prod_{j=1}^n \dim V_{r_j,s_j,\,[k_j]}
\cdot F(r_1 s_1, \ldots, r_n s_n)
\]
where $F$ encodes the fusion multiplicities from the Verlinde formula
(depending only on module labels, not on~$h$), and the sum is over
non-negative integers~$k_j$. Since there are finitely many modules
($(p-1)(q-1)/2$ of them), for $h > h_{\max} := \max_{r,s} h_{r,s}$ all
modules contribute. By Step~2, each factor $\dim V_{r_j,s_j,\,[k_j]}$
is $N$-periodic in~$k_j$ for large~$k_j$. Under $h \mapsto h + N$ the
constraint shifts to $\sum k_j = h + N - \sum h_{r_j,s_j}$, and the
$N$-periodicity of each weight-space dimension gives
$\dim \bar{B}^{(n)}_{[h+N]} = \dim \bar{B}^{(n)}_{[h]}$ for $h \gg 0$.

It remains to show that the bar \emph{cohomology} dimensions, not just the
chain-space dimensions, are periodic. The bar differential
$d \colon \bar{B}^{(n)}_{[h]} \to \bar{B}^{(n+1)}_{[h]}$ is determined by the
OPE structure constants of $M(p,q)$. For minimal models, three-point functions
on the sphere factor as a fusion multiplicity times a universal Virasoro
conformal block contribution. The conformal block at relative weights
$(k_1, k_2, k_3)$ is a rational function of the conformal weights~$h_{r,s}$
and the relative weights~$k_j$, determined by the Shapovalov form. By the
same theta-function periodicity as in Step~2, the matrix entries of~$d$ at
weight~$h+N$ are identified with those at weight~$h$ via the canonical
isomorphism $V_{r,s,\,[k+N]} \cong V_{r,s,\,[k]}$ (which respects the
Virasoro module structure at the level of the weight-space basis). Therefore
$\ker d$ and $\operatorname{im} d$ at weight $h+N$ are isomorphic to those at
weight~$h$, giving
$\dim H^n(\bar{B}_{[h+N]}^{\mathrm{ch}}) = \dim H^n(\bar{B}_{[h]}^{\mathrm{ch}})$
for all $h$ sufficiently large.
\end{evidence}

\begin{conjecture}[Modular periodicity for general rational chiral algebras; \ClaimStatusConjectured]
\label{conj:modular-periodicity}
\index{periodicity!modular|textbf}
Let $\cA$ be a rational chiral algebra with central charge $c = p/q$, $\gcd(p,q) = 1$. Set
\[
N \;=\; \frac{24q}{\gcd(p,24)}.
\]
Then for all bar degrees $n$ and all sufficiently large conformal weight $h$:
\[
\dim H^n(\bar{B}_{[h+N]}^{\mathrm{ch}}(\cA))
\;=\;
\dim H^n(\bar{B}_{[h]}^{\mathrm{ch}}(\cA)).
\]
\end{conjecture}

\begin{remark}[Scope and examples]\label{rem:modular-periodicity-scope}
Steps~1 and~3 are proved for minimal models and WZW; the gap is Step~2 (convolution with $1/\eta$). Examples: Ising $N \mid 48$, $\widehat{\mathfrak{sl}}_2$ at $k=1$ gives $N=24$.
\end{remark}

\begin{conjecture}[Modular periodicity for WZW models; \ClaimStatusConjectured]
\label{conj:modular-periodicity-wzw}
\index{periodicity!modular!WZW models|textbf}
\index{WZW model!modular periodicity|textbf}
Let $\widehat{\mathfrak{g}}_k$ be an affine Kac--Moody algebra at
positive integer level $k \geq 1$, with $\mathfrak{g}$ a finite-dimensional
simple Lie algebra of rank~$r$. Write the central charge
$c = k\dim(\mathfrak{g})/(k + h^\vee) = p/q$ in lowest terms and set
\[
N \;=\; \frac{24q}{\gcd(p,24)}.
\]
Then for all bar degrees~$n$ and all sufficiently large conformal
weight~$h$:
\[
\dim H^n(\bar{B}_{[h+N]}^{\mathrm{ch}}(\widehat{\mathfrak{g}}_k))
\;=\;
\dim H^n(\bar{B}_{[h]}^{\mathrm{ch}}(\widehat{\mathfrak{g}}_k)).
\]
\end{conjecture}

\begin{evidence}
The same three-step strategy as Conjecture~\ref{conj:modular-periodicity-minimal} applies, using the Weyl--Kac character formula (Kac~\cite[\S12.7]{Kac}) in place of Rocha-Caridi. Step~1 ($T^N = \mathrm{Id}$) holds since $h_\lambda = \langle \lambda, \lambda + 2\rho\rangle / 2(k+h^\vee)$ is rational with denominator dividing $24(k+h^\vee)$. Step~2: the level-$(k+h^\vee)$ theta functions in the Weyl--Kac numerator have $N$-periodic Fourier coefficients. Step~3: the bar differential is controlled by quantum Clebsch--Gordan coefficients via the KL equivalence (Kazhdan--Lusztig~\cite{KL93}), and $q^{2(k+h^\vee)}=1$ ensures the same periodicity.
\end{evidence}

\begin{remark}[Scope]\label{rem:wzw-periodicity-scope}
$T$-matrix periodicity (Step~1) is unconditional for both minimal
models and WZW. The gap is Step~2: convolution with $1/\eta$ does
not preserve eventual periodicity. General rational chiral algebras
remain open.
(Part of the MC2 theorem package; Theorem~\ref{thm:mc2-full-resolution}.)
\end{remark}

\subsubsection{Koszul dual behavior}

\begin{conjecture}[Reflected modular periodicity; \ClaimStatusConjectured]\label{conj:reflected-modular-periodicity}
\index{reflected modular periodicity}
If $\mathcal{A}$ has rational central charge $c = p/q$ and modular period $N = 24q/\gcd(p,24)$, and its Koszul dual $\mathcal{A}^!$ has central charge $c' = p'/q'$ (determined by the level duality $k \mapsto k' = -k - 2h^\vee$ via the Sugawara formula) and modular period $N' = 24q'/\gcd(p',24)$, then:
\begin{equation}\label{eq:period-sum}
\frac{1}{N} + \frac{1}{N'} = \frac{\gcd(p,24) + \gcd(p',24)}{24q}
\end{equation}
where $q' = q$ whenever $\gcd(26q - p, q) = 1$ (which holds when $\gcd(p,q) = 1$).
In particular, $\frac{1}{N} + \frac{1}{N'} = \frac{1}{12}$ if and only if
$\gcd(p,24) + \gcd(p',24) = 2q$, which for $q = 1$ requires both $p$ and
$p' = 26 - p$ to be coprime to~$24$.
\end{conjecture}

\begin{remark}[Precise hypotheses]
\label{rem:precise-reflected-hypotheses}
The conjecture requires the following hypotheses to be well-posed:
\begin{enumerate}
\item $\cA$ is a rational chiral algebra (finitely many irreducible modules) with $c = p/q \in \mathbb{Q}$, $\gcd(p,q) = 1$.
\item $\cA$ admits a Koszul dual $\cA^!$ in the sense of Definition~\ref{def:chiral-koszul-pair}, with $\cA^!$ also rational.
\item The modular periods $N$, $N'$ are defined as the minimal positive integers such that $T^N$ acts trivially on the space of characters of $\cA$, $\cA^!$ respectively, where $T: \tau \mapsto \tau + 1$.
\item When $\cA$ arises from an affine Lie algebra at level $k$, the dual central charge $c' = c(\cA^!)$ is determined from the dual level $k' = -k - 2h^\vee$ via the Sugawara formula $c' = k'\dim(\mathfrak{g})/(k' + h^\vee)$.
\end{enumerate}
The relation~\eqref{eq:period-sum} is verified for the Heisenberg algebra ($c = c' = 1$, $N = N' = 24$, sum $= 1/12$) and for the $\widehat{\mathfrak{sl}}_2$ WZW model at level $k = 1$ ($c = 1$, $c' = 1$, $N = N' = 24$). For $c = 5$, $c' = 21$ (both coprime to~$24$ but $\gcd(21, 24) = 3$), one gets $N = 24$, $N' = 8$, and $1/N + 1/N' = 1/6 \neq 1/12$, showing the special case $1/N + 1/N' = 1/12$ requires both $p$ and $p'$ coprime to~$24$.
\end{remark}

\begin{remark}[Scope]
The formula~\eqref{eq:period-sum} depends on Conjecture~\ref{conj:modular-periodicity}; the principal obstruction is that Koszul duality need not preserve rationality. Part of MC2 (Theorem~\ref{thm:mc2-full-resolution}).
\end{remark}

\subsection{Type II: quantum group periodicity}

\subsubsection{The quantum group structure}

\begin{proposition}[Quantum periodicity profile under admissible-level
 KL/DS transport; \ClaimStatusProvedHere]
\label{prop:periodicity-quantum-input}
\index{periodicity!quantum|textbf}
Let $\mathcal{W}^k(\mathfrak{g})$ be the W-algebra at admissible level $k = -h^{\vee} + p/q$ where $h^{\vee}$ is the dual Coxeter number, $p \geq h^\vee$, $q \geq h^\vee$, $\gcd(p,q) = 1$. Then the quantum integers, quantum dimensions, and fusion coefficients (transported through the KL/DS interface) recur with period dividing
\[
M = 2h^{\vee}pq/\gcd(p,q,h^{\vee}).
\]
This records only the Type~II quantum input to the periodicity profile $(N_{\mathrm{mod}}, N_{\mathrm{quant}})$; upgrading to full bar complex periodicity requires a separate OPE transport theorem.
\end{proposition}

\begin{proof}
At admissible level $k = -h^\vee + p/q$, we write $q_{\mathrm{KL}} = \exp(\pi i/(k + h^\vee)) = \exp(\pi i \cdot q/p)$ for the Kazhdan--Lusztig quantum parameter. Since $\gcd(p,q) = 1$, this $q_{\mathrm{KL}}$ is a root of unity of order dividing $2p$.

\emph{Step 1: Semisimplicity.}
By Arakawa's theorem \cite{Ara07}, the category $\mathcal{O}_k(\mathcal{W}^k(\mathfrak{g}))$ at admissible level is semisimple with finitely many simple objects, indexed by the admissible weights.

\emph{Step 2: Kazhdan--Lusztig equivalence and DS reduction.}
The Kazhdan--Lusztig equivalence \cite{KL93} provides a braided tensor equivalence $\mathcal{O}_k(\widehat{\mathfrak{g}}) \simeq \mathcal{C}(U_q(\mathfrak{g}))$, where $\mathcal{C}(U_q(\mathfrak{g}))$ is the semisimplified tilting quotient (Remark~\ref{rem:kl-target-category}) with quantum parameter $q = \exp(\pi i/(k + h^\vee))$. The Drinfeld--Sokolov reduction functor $H^0_{Q_{\mathrm{DS}}} \colon \mathcal{O}_k(\widehat{\mathfrak{g}}) \to \mathcal{O}_k(\mathcal{W}^k(\mathfrak{g}))$ is exact at admissible levels (Arakawa~\cite{Ara07}), and the composition transports the bar complex structure from $\widehat{\mathfrak{g}}$-modules to $\mathcal{W}^k(\mathfrak{g})$-modules.

\emph{Step 3: Quantum integer periodicity.}
The quantum integers $[n]_{q_{\mathrm{KL}}} = (q_{\mathrm{KL}}^n - q_{\mathrm{KL}}^{-n})/(q_{\mathrm{KL}} - q_{\mathrm{KL}}^{-1})$ satisfy $[n + 2\ell]_{q_{\mathrm{KL}}} = [n]_{q_{\mathrm{KL}}}$ where $\ell$ is the order of $q_{\mathrm{KL}}^2 = \exp(2\pi i q/p)$ as a root of unity; since $\gcd(p,q) = 1$, this order is $\ell = p$.

The quantum dimension of the simple module $L(\lambda)$ is the Weyl character formula:
\[
\dim_q L(\lambda) = \prod_{\alpha \in \Delta^+}
\frac{[\langle \lambda + \rho, \alpha^\vee \rangle]_{q_{\mathrm{KL}}}}
 {[\langle \rho, \alpha^\vee \rangle]_{q_{\mathrm{KL}}}}.
\]
This is a product of $|\Delta^+|$ quantum integers with arguments determined by the weight~$\lambda$. The periodicity of each factor gives $\dim_q L(\lambda + 2\ell\rho) = \dim_q L(\lambda)$, so the quantum dimensions (hence fusion coefficients via the Verlinde formula) are periodic in $\lambda$ with period $2\ell\rho = 2p\rho$.

The admissible weights are indexed by pairs $(r,s)$ with $0 \leq r \leq p - h^\vee$ and $0 \leq s \leq q - h^\vee$ (for generic simple~$\mathfrak{g}$; the precise range depends on $\Delta^+$). Combining the three sources
\begin{enumerate}[label=(\alph*)]
\item quantum integer period: $2\ell = 2p$,
\item Weyl group orbit: $|W|$ copies with inner period $h^\vee$ (from $\langle \rho, \alpha^\vee_{\max} \rangle = h^\vee - 1$),
\item $q$-restricted weight lattice: period~$q$,
\end{enumerate}
we obtain a common period dividing
$M = 2h^\vee pq / \gcd(p,q,h^\vee)$ for the quantum integers, quantum
dimensions, and fusion data transported through the admissible-level
KL/DS interface.
\end{proof}

\begin{example}[Quantum periodicity for
\texorpdfstring{$\widehat{\mathfrak{sl}}_2$}{sl-hat_2} at \texorpdfstring{$k = -1/2$}{k = -1/2}]
\label{ex:hh-sl2-admissible}
\index{Hochschild cohomology!admissible level}
\index{sl2-hat@$\widehat{\mathfrak{sl}}_2$!Hochschild cohomology}
At the admissible level $k = -1/2$ ($p = 3$, $q = 2$,
$h^\vee = 2$), the quantum parameter is
$q_{\mathrm{KL}} = \exp(\pi i \cdot 2/3) = e^{2\pi i/3}$
(a primitive third root of unity). The Kazhdan--Lusztig
category $\mathcal{O}_k$ is semisimple with $2$ simple modules
(Example~\ref{ex:sl2-admissible}), and the quantum dimensions are:
\[
\dim_q(\mathcal{L}_0) = 1, \qquad
\dim_q(\mathcal{L}_1) = [2]_q = q + q^{-1} = -1
\]
(using $q = e^{2\pi i/3}$, so $[2]_q = 2\cos(2\pi/3) = -1$).

The quantum integer periodicity has $\ell = 3$
($[n+6]_q = [n]_q$, since $q^2 = e^{4\pi i/3}$ has order~$3$).
The period is $M = 2 \cdot 2 \cdot 3 \cdot 2 / \gcd(3,2,2) = 24$.

The chiral Hochschild cohomology of
$L_{-1/2}(\mathfrak{sl}_2)$ has:
\begin{align}
\ChirHoch^0 &= \mathbb{C} & & \text{(center)}, \\
\ChirHoch^1 &= 0 & & \text{(no outer derivations)}, \\
\ChirHoch^2 &= \mathbb{C} & & \text{(one marginal deformation: the
 level)},
\end{align}
The deformation in $\ChirHoch^2$ corresponds to the level family $k \mapsto k + t$; the vanishing $\ChirHoch^1 = 0$ reflects rigidity (no outer derivations).
The quantum period $M = 24$ manifests not in $\ChirHoch^n$ (which
vanishes for $n > 2$ by Theorem~\ref{thm:hochschild-polynomial-growth})
but in the \emph{weight-graded bar complex cohomology}:
$\dim H^n(\bar{B}^{\mathrm{ch}}_{[h+24]}) = \dim H^n(\bar{B}^{\mathrm{ch}}_{[h]})$
for $h \gg 0$ (Conjecture~\ref{conj:modular-periodicity}).
\end{example}

\subsection{Type III: geometric tautological depth}

\subsubsection{Genus dependence and nilpotent depth}

The geometric contribution to bar cohomology from higher genus provides \emph{bounded tautological depth} rather than periodicity: the Kodaira--Spencer operator is nilpotent and the bar spectral sequence terminates after finitely many steps.

\begin{theorem}[Geometric tautological depth bound; \ClaimStatusProvedHere]
\label{thm:geometric-periodicity-weak}
\index{periodicity!geometric!tautological depth|textbf}
\index{tautological depth!geometric|textbf}
For a chiral algebra $\mathcal{A}$ on a genus $g \geq 2$ curve $X$,
the Kodaira--Spencer image of the Hodge class is nilpotent:
\[
\kappa(c_1(\mathbb{E}))^{3g-2} = 0
\quad \text{in } \ChirHoch^*(\mathcal{A}).
\]
In particular, the geometric direction of the bar spectral sequence
has bounded tautological depth: at most $3g - 3$ nontrivial geometric
filtration layers can contribute.

At $g = 0$, no Hodge bundle contributes; at $g = 1$, the relation
$c_1(\mathbb{E}) = \frac{1}{12}\delta$ absorbs the Hodge
contribution into the modular data.
\end{theorem}

\begin{proof}
The Kodaira--Spencer map (Theorem~\ref{thm:kodaira-spencer-chiral-complete}) provides a ring homomorphism
\[
\kappa \colon H^*(\overline{\mathcal{M}}_g, \mathbb{Q}) \longrightarrow \ChirHoch^*(\mathcal{A})
\]
whose image controls the geometric contributions to bar cohomology.
The geometric operator $\sigma_{\mathrm{geom}}$ acts via
multiplication by $\kappa(\lambda)$, where
$\lambda = c_1(\mathbb{E})$ is the first Chern class of the Hodge
bundle $\mathbb{E} \to \overline{\mathcal{M}}_g$.

Since $\dim_{\mathbb{C}} \overline{\mathcal{M}}_g = 3g - 3$, every cohomology class of degree exceeding $2(3g-3) = 6g - 6$ vanishes. In particular,
\[
\lambda^{3g-2} = c_1(\mathbb{E})^{3g-2} = 0 \quad \text{in } H^{2(3g-2)}(\overline{\mathcal{M}}_g, \mathbb{Q}),
\]
since $2(3g-2) = 6g - 4 > 6g - 6$ for all $g \geq 2$. Applying $\kappa$:
\[
\kappa(\lambda)^{3g-2} = \kappa(\lambda^{3g-2}) = \kappa(0) = 0 \quad \text{in } \ChirHoch^*(\mathcal{A}).
\]
Therefore $\sigma_{\mathrm{geom}}$ is nilpotent of index at most $3g - 2$, giving at most $3g - 3$ nontrivial filtration steps. At $g = 0$ there is no Hodge bundle; at $g = 1$, $c_1(\mathbb{E}) = \frac{1}{12}\delta$ absorbs into $N_{\mathrm{mod}}$.
\end{proof}

\begin{remark}[Nilpotent depth vs.\ periodicity]
\label{rem:nilpotent-vs-periodic}
\index{tautological depth!vs.\ periodicity}
$\sigma_{\mathrm{geom}}$ is nilpotent ($\sigma^N = 0$), not periodic ($\sigma^N = \mathrm{id}$): the geometric contribution provides a stabilization threshold (cf.\ Remark~\ref{rem:stratified-periodicity}).
\end{remark}

\begin{theorem}[Sharp geometric depth on smooth moduli; \ClaimStatusProvedHere]
\label{thm:geometric-depth-smooth}
\index{tautological depth!sharp bound on $\mathcal{M}_g$|textbf}
\index{Graber--Vakil vanishing}
For a chiral algebra $\mathcal{A}$ on a smooth genus $g \geq 2$
curve, suppose the Kodaira--Spencer map factors through the
cohomology of the smooth moduli space:
\[
\kappa \colon H^*(\mathcal{M}_g, \mathbb{Q}) \longrightarrow
\ChirHoch^*(\mathcal{A}).
\]
Then the nilpotency index of $\kappa(\lambda)$ is at most~$g - 1$:
\begin{equation}\label{eq:sharp-geometric-depth}
\kappa(c_1(\mathbb{E}))^{g-1} = 0
\quad \text{in } \ChirHoch^*(\mathcal{A}).
\end{equation}
In particular:
\begin{enumerate}[label=\textup{(\alph*)}]
\item At genus~$2$, the Hodge class contribution vanishes entirely:
 $\kappa(\lambda) = 0$.
\item At genus~$3$, the geometric depth is at most~$2$
 (compared to~$7$ from the compactified bound).
\item In general, the sharp bound $g - 1$ improves the
 compactified bound $3g - 2$ by a factor of approximately~$3$.
\end{enumerate}
\end{theorem}

\begin{proof}
The tautological ring $R^*(\mathcal{M}_g)$ of the smooth
moduli space satisfies the Graber--Vakil vanishing
theorem~\cite{GraVak05} (extending Looijenga~\cite{Looij95}):
\begin{equation}\label{eq:graber-vakil-vanishing}
R^d(\mathcal{M}_g) = 0 \quad \text{for } d > g - 2.
\end{equation}
The Hodge class $\lambda = c_1(\mathbb{E})$ is a
tautological class of degree~$1$.
On the smooth moduli space, the Mumford relation reduces to
$\lambda|_{\mathcal{M}_g} = \kappa_1/12$
(since the boundary class $\delta$ vanishes on
$\mathcal{M}_g$). Therefore
\[
\lambda^{g-1} \in R^{g-1}(\mathcal{M}_g) = 0
\]
since $g - 1 > g - 2$. Applying $\kappa$:
\[
\kappa(\lambda)^{g-1} = \kappa(\lambda^{g-1}) = 0.
\]

For genus~$2$: $g - 1 = 1$, so $\lambda^1 = \lambda \in
R^1(\mathcal{M}_2)$. Since $R^d(\mathcal{M}_2) = 0$ for
$d > 0$, we get $\lambda|_{\mathcal{M}_2} = 0$, hence
$\kappa(\lambda) = 0$.
This means the Hodge class produces no geometric correction
to bar cohomology at genus~$2$: the genus-$2$ bar complex, at
the level of the Hodge class contribution, is determined
entirely by the genus-$0$ data.
\end{proof}

\begin{remark}[Factorization hypothesis]
\label{rem:factorization-hypothesis-geom}
The factorization through $H^*(\mathcal{M}_g)$ holds on smooth
curves. On $\overline{\mathcal{M}}_g$, boundary divisor classes
$\delta_i$ can increase nilpotent depth beyond $g-1$ (but never
beyond $3g-2$, Theorem~\ref{thm:geometric-periodicity-weak}).
\end{remark}

\begin{conjecture}[Geometric amplitude on compactified moduli; \ClaimStatusConjectured]
\label{conj:geometric-periodicity}
\index{tautological depth!sharp bound on $\overline{\mathcal{M}}_g$|textbf}
For a Koszul chiral algebra~$\mathcal{A}$
on $\overline{\mathcal{M}}_g$
with factorization extensions to the boundary, the nilpotency
index of the geometric operator $\kappa(\lambda)$ on
$\overline{\mathcal{M}}_g$ is controlled by the Mumford
relation $12\lambda = \kappa_1 + \delta$:
the boundary contribution $\kappa(\delta)$ increases the
nilpotency index beyond the interior bound $g - 1$ by at most
the depth of the boundary tautological ring. Precisely, there
exists a function $\mathrm{nil}_{\partial}(g)$, depending only
on the genus, such that:
\[
\mathrm{nil}(\kappa(\lambda)) \;\leq\; (g-1) + \mathrm{nil}_{\partial}(g),
\qquad \mathrm{nil}_{\partial}(g) \leq 2g - 1.
\]
The additive structure reflects the Mumford decomposition
$12\lambda = \kappa_1 + \delta$, with the interior contributing
at most $g - 1$ (proved) and the boundary contributing
$\mathrm{nil}_{\partial}(g)$ additional layers.
\end{conjecture}

\begin{remark}[Scope and provenance]\label{rem:geometric-periodicity-scope}
The interior bound $g-1$ is proved
(Theorem~\ref{thm:geometric-depth-smooth}, Graber--Vakil); the
compactified bound $3g-2$ is proved
(Theorem~\ref{thm:geometric-periodicity-weak}). The conjecture
interpolates via the Mumford relation. The geometric contribution
is nilpotent ($\sigma^N = 0$), not periodic ($\sigma^N = \mathrm{id}$);
true periodicity arises from Types~I and~II only.
(Part of the MC2 theorem package; Theorem~\ref{thm:mc2-full-resolution}.)
\end{remark}

\subsubsection{Examples at different genera}

\begin{example}[Genus \texorpdfstring{$0$}{0}: the sphere]
No geometric tautological depth (simply connected, no moduli).
\end{example}

\begin{example}[Genus \texorpdfstring{$1$}{1}: the torus]
For elliptic curve $E_{\tau}$:
\begin{itemize}
\item Period lattice $\Lambda = \mathbb{Z} + \tau\mathbb{Z}$
\item Four spin structures (fermions have period 8)
\item Modular parameter $\tau$ gives $SL_2(\mathbb{Z})$ action
\end{itemize}

Free fermion on $E_{\tau}$: the weight-graded bar complex cohomology satisfies
\[
\dim H^n(\bar{B}^{\mathrm{ch}}_{[h+8]}(\mathcal{F},\, E_{\tau}))
\;=\;
\dim H^n(\bar{B}^{\mathrm{ch}}_{[h]}(\mathcal{F},\, E_{\tau}))
\quad\text{for } h \gg 0.
\]
The period~$8$ comes from: $4$ spin structures $\times$ $2$ (fermion parity).
(The total $\ChirHoch^n(\mathcal{F})$ vanishes for $n > 2$ by
Theorem~\textup{\ref{thm:hochschild-polynomial-growth}}; the periodicity
is in conformal weight, not in Hochschild degree.)
The Hodge class is absorbed into the modular data via
$c_1(\mathbb{E}) = \frac{1}{12}\delta$.
\end{example}

\begin{example}[Genus 2: Hodge class vanishing]
\label{ex:genus2-hodge-vanishing}
By Theorem~\ref{thm:geometric-depth-smooth}, the Hodge class
contribution vanishes entirely at genus~$2$:
$\kappa(\lambda) = 0$ in $\ChirHoch^*(\mathcal{A})$. This follows from
the Graber--Vakil vanishing $R^d(\mathcal{M}_2) = 0$ for $d > 0$.
The genus-$2$ bar complex receives no geometric corrections from
$c_1(\mathbb{E})$; any higher-genus modifications at $g = 2$ must
arise from other tautological classes or from boundary
contributions on $\overline{\mathcal{M}}_2$ (which reduce to
$\mathcal{M}_{1,1} \times \mathcal{M}_{1,1}$ and
$\mathcal{M}_{1,2}$ data).
\end{example}

\subsection{Stratified periodicity}

This subsection separates the unconditional structural part of the
periodicity story from the conditional numerical values.

\begin{conjecture}[Stratified periodicity package (partial); \ClaimStatusConjectured]
\label{conj:complete-periodicity-classification}
\index{periodicity!classification (partial)|textbf}
\index{periodicity!stratified}
For a rational chiral algebra $\mathcal{A}$ on a genus~$g$ curve with
central charge $c = p/q$ ($\gcd(p,q) = 1$) and quantum group level
inducing period~$M$, the bar cohomology dimensions are eventually
periodic in conformal weight:
\[
\text{Period}(\mathcal{A}) \mid
\text{lcm}(N_{\text{modular}}, N_{\text{quantum}})
\]
where:
\begin{align}
N_{\text{modular}} &= \frac{24q}{\gcd(p, 24)} \quad
 \text{(Conjectures~\ref{conj:modular-periodicity-minimal},
 \ref{conj:modular-periodicity-wzw} for minimal/WZW;
 Conjecture~\ref{conj:modular-periodicity} in general)} \\
N_{\text{quantum}} &= M \text{ (from quantum group; proved)}
\end{align}
and the conformal weight threshold beyond which this periodicity
holds is controlled by the geometric tautological depth
$\mathrm{nil}(\kappa(\lambda)) \leq g - 1$
(Theorem~\ref{thm:geometric-depth-smooth}).
\end{conjecture}

\begin{evidence}
The unconditional content is structural rather than numerical.
What is proved is the Type~II quantum input and the tautological
depth bound. What remains conjectural is the sharp Type~I modular
input.

The bar spectral sequence
\[
E_2^{p,q} = H^q(\overline{C}_{p+2}(X))
 \otimes H^0(\mathcal{A}^{\otimes(p+2)})
\]
admits a tridegree decomposition
$\bigl(d_{\mathrm{mod}}, d_{\mathrm{quant}}, d_{\mathrm{geom}}\bigr)$,
where the three indices record respectively the representation-theoretic
weight, the fusion-theoretic degree, and the configuration-space
cohomological degree.

\emph{Step~1: Inputs.}
\begin{enumerate}
\item \emph{Modular (Type~I).} For the rational families treated
 above, Step~1 of
 Conjectures~\ref{conj:modular-periodicity-minimal}
 and~\ref{conj:modular-periodicity-wzw} proves only the
 $T$-matrix phase bound on the finite-dimensional character space.
 Upgrading that phase bound to eventual periodicity of the bar
 cohomology with order~$N_{\mathrm{mod}}$ is precisely the
 conjectural input of the Type~I modular-periodicity package.
\item \emph{Quantum (Type~II).} The quantum-integer periodicity
 $[n + 2\ell]_q = [n]_q$ is theorematic in the admissible-level
 KL/DS regime of Proposition~\ref{prop:periodicity-quantum-input}, so
 the Type~II profile contributes a proved
 $N_{\mathrm{quant}}$ factor.
\item \emph{Geometric (Type~III).}
 Theorem~\ref{thm:geometric-depth-smooth} proves
 $\kappa(\lambda)^{g-1} = 0$ on smooth moduli, giving a
 sharp tautological depth bound. This is a \emph{nilpotent
 stabilization}, not a periodicity source: it bounds the
 transient before modular/quantum periodicity takes hold,
 rather than contributing a periodic factor to the lcm
 (Remark~\ref{rem:nilpotent-vs-periodic}).
\end{enumerate}

\emph{Step~2: Structural mechanism.}
The genuine periodicity operators
$\sigma_{\mathrm{mod}}$ and $\sigma_{\mathrm{quant}}$
act on the first two tridegree directions. Their combined order
divides
$\mathrm{lcm}(N_{\mathrm{mod}}, N_{\mathrm{quant}})$.
The geometric direction is \emph{bounded}, not periodic: the
nilpotent operator $\sigma_{\mathrm{geom}} = \kappa(\lambda)$
satisfies $\sigma_{\mathrm{geom}}^{g-1} = 0$
(Theorem~\ref{thm:geometric-depth-smooth}), so the
geometric spectral sequence has at most $g - 2$ nontrivial
filtration steps.

The bookkeeping separation is:
\begin{itemize}
\item the modular input acts on the representation-theoretic component
 via $T$-eigenvalues / conformal weights (periodic, conjectural);
\item the quantum input acts on the fusion-theoretic component via
 quantum dimensions and Clebsch--Gordan data (periodic, proved);
\item the geometric input acts on the configuration-space component via
 tautological classes on $\mathcal{M}_g$ (\emph{nilpotent}, proved).
\end{itemize}

\emph{Step~3: Combined structure.}
The genuine period of $\mathcal{A}$ is governed by the periodic
operators only:
$\mathrm{Period}(\mathcal{A}) \mid \mathrm{lcm}(N_{\mathrm{mod}},
N_{\mathrm{quant}})$. The geometric contribution controls
the \emph{stabilization threshold}: bar cohomology dimensions
become $\mathrm{Period}(\mathcal{A})$-periodic in conformal weight
once the weight exceeds a threshold determined by the tautological
depth. On $\overline{\mathcal{M}}_g$ the depth is at most $3g-2$
(Theorem~\ref{thm:geometric-periodicity-weak}); on $\mathcal{M}_g$
the sharp bound is $g-1$
(Theorem~\ref{thm:geometric-depth-smooth}).
\end{evidence}

\begin{remark}[Scope]\label{rem:periodicity-classification-scope}
Conjectured because the modular bound
(Conjecture~\ref{conj:modular-periodicity}) is open. Quantum
periodicity is proved; the geometric contribution is nilpotent depth
(proved), not a periodic source. The lcm formula
$\mathrm{Period}(\cA) \mid
\mathrm{lcm}(N_{\mathrm{mod}}, N_{\mathrm{quant}})$ is the correct
statement.
(Part of the MC2 theorem package; Theorem~\ref{thm:mc2-full-resolution}.)
\end{remark}

\begin{remark}[Periodicity profile refinement]\label{rem:periodicity-triple-deformation}
\index{periodicity profile!refinement}
The scalar period is the shadow of the richer profile
$\Pi(\cA) = (M_\cA, Q_\cA, G_\cA)$
(Remark~\ref{rem:periodicity-triple}):
$M_\cA$ carries the modular $T$-eigenvalue action (conjectural),
$Q_\cA$ encodes quantum CG periodicity (proved), and $G_\cA$
encodes the nilpotent tautological depth
(Theorem~\ref{thm:geometric-depth-smooth}).
\end{remark}

\begin{remark}[Stratified periodicity]\label{rem:stratified-periodicity}
\index{periodicity!stratified reformulation}
The mature formulation separates periodic from nilpotent contributions:
(a)~the lcm mechanism for the two genuine periodic sources is proved
(Proposition~\ref{prop:periodicity-exchange-koszul}); quantum
periodicity is explicit; geometric depth $\leq g-1$
(Theorem~\ref{thm:geometric-depth-smooth}) is proved.
(b)~Minimal models and WZW have explicit $T$-matrix periodicity,
but bar-periodicity remains conjectural
(Conjectures~\ref{conj:modular-periodicity-minimal},
\ref{conj:modular-periodicity-wzw}: Step~2 gap).
(c)~For general Koszul chiral algebras, the period divides
$\mathrm{lcm}(N_{\mathrm{mod}}, N_{\mathrm{quant}})$; the spectral
radius of $T_{\mathrm{rec}}$ bounds $N_{\mathrm{mod}}$
(Theorem~\ref{thm:dominant-branch-point}).
See the editorial companion for the full research programme.
\end{remark}

\subsection{Koszul duality and periodicity interaction}

\begin{proposition}[Periodicity-profile transport under Koszul duality;
 \ClaimStatusProvedHere]
\index{periodicity!exchange under duality}
\label{prop:periodicity-exchange-koszul}
Let $(\cA, \cA^!)$ be a Koszul dual pair of rational chiral algebras on a genus~$g$ curve~$X$. Then:
\begin{enumerate}
\item The geometric tautological depth is unchanged:
 $\mathrm{nil}(\kappa(\lambda))_{\cA} =
 \mathrm{nil}(\kappa(\lambda))_{\cA^!}$.
\item The dual modular phase bound is determined by the dual central
 charge: $N'_{\text{mod}} = 24q'/\gcd(p', 24)$ where
 $c' = c(\cA^!) = p'/q'$ in lowest terms.
\item If both algebras lie in the admissible-level KL/DS regime of
 Type~II above, then the quantum periodicity input is preserved:
 $N_{\text{quant}}(\cA) = N_{\text{quant}}(\cA^!)$.
\end{enumerate}
In particular, Koszul duality transports the periodicity \emph{profile}
$(N_{\text{mod}}, N_{\text{quant}})$ and the geometric depth
component-wise; it
does not assert equality of scalar periods, since the modular component
changes with the dual central charge. Whenever both periodic profile
components are defined, the total period of $\cA^!$ divides
$\mathrm{lcm}(N'_{\text{mod}}, N_{\text{quant}})$.
\end{proposition}

\begin{proof}
\emph{(1) Geometric tautological depth is unchanged.}
Both $\cA$ and $\cA^!$ live on the same curve $X$. The Hodge bundle contribution from $\overline{\mathcal{M}}_g$ (via the Kodaira--Spencer map, Theorem~\ref{thm:kodaira-spencer-chiral-complete}) depends only on the geometry of~$X$, not on the chiral algebra. Since $\kappa(\lambda)$ is the image of $\lambda = c_1(\mathbb{E})$ under the same ring homomorphism for both $\cA$ and $\cA^!$, the nilpotency index is preserved.

\emph{(2) Modular period of the dual.}
The dual central charge $c'$ is determined by the level duality $k \mapsto k' = -k - 2h^\vee$ via the Sugawara formula, giving $c' = p'/q'$ in lowest terms. The $T$-matrix of~$\cA^!$ has eigenvalues $e^{2\pi i(h'_\lambda - c'/24)}$, and the same elementary argument as in Step~1 of the periodicity proofs (requiring only $c'N'/24 \in \mathbb{Z}$ and rationality of conformal weights) gives $T^{N'} = \mathrm{Id}$ for $N'_{\text{mod}} = 24q'/\gcd(p',24)$. This $T$-matrix periodicity is unconditional: it depends only on rationality of~$c'$, not on any conjecture about bar cohomology.

\emph{(3) Quantum input in the admissible-level regime.}
In the Type~II admissible-level KL/DS regime, the quantum component is
encoded by quantum integers, quantum dimensions, and fusion data.
Koszul duality sends level $k$ to $k' = -k - 2h^\vee$, hence
$q \mapsto q^{-1}$. Since $[n]_{q^{-1}} = [n]_q$ for all $n$, the
Type~II quantum input is preserved under duality whenever that regime
applies.
\end{proof}

\begin{remark}[Modular period exchange]\label{rem:periodicity-exchange-harmonic}
% backward-compatible label removed (was conj:periodicity-exchange-harmonic)
Proposition~\ref{prop:periodicity-exchange-koszul} establishes
unconditionally that the geometric tautological depth is preserved and
that the dual modular phase bound is determined by the dual central
charge. In the admissible-level KL/DS regime it also preserves the
Type~II quantum input. The sum of reciprocal modular periods is given by
Conjecture~\ref{conj:reflected-modular-periodicity}: writing $c = p/q$
and $c' = p'/q'$,
\[
\frac{1}{N_{\text{mod}}} + \frac{1}{N'_{\text{mod}}}
= \frac{\gcd(p,24) + \gcd(p',24)}{24q}.
\]
This equals $\frac{1}{12}$ precisely when $\gcd(p,24) + \gcd(p',24) = 2q$; for $q = 1$ and $c + c' = 26$, this requires both $p$ and $26 - p$ coprime to~$24$ (e.g.\ $c = 1$, $c' = 25$ or $c = 7$, $c' = 19$, but \emph{not} $c = 5$, $c' = 21$ since $\gcd(21, 24) = 3$).
\end{remark}



\section{Physical applications}

\subsection{Marginal deformations in CFT}

In 2D conformal field theory, $\ChirHoch^2(\mathcal{A})$ classifies marginal deformations
$S \to S + \lambda \int_{\Sigma} \phi(z,\bar{z}) d^2z$.
Conformal invariance is preserved when $\phi$ has weight $(1,1)$ (marginality), $[\phi] \in \ChirHoch^2$ is a cocycle (preserving the OPE algebra), and the obstruction in $\ChirHoch^3$ vanishes (extending to all orders).

\begin{example}[Exactly marginal deformations]
For the free boson, $\ChirHoch^2 = \mathbb{C}$ gives the radius deformation; for $\mathcal{N}=4$ SYM, $\ChirHoch^2 = \mathbb{C}^{3(g-1)}$ gives gauge coupling and theta angles; for minimal models, $\ChirHoch^2 = 0$ (isolated in moduli space).
\end{example}

\subsection{String field theory}

The $A_{\infty}$ structure encoded in Hochschild cohomology gives string field theory vertices:

\begin{theorem}[String field theory from Hochschild {\cite{Zwi93}}; \ClaimStatusProvedElsewhere]\label{thm:string-field-theory-hochschild}
The operations $m_n: \mathcal{A}^{\otimes n} \to \mathcal{A}[2-n]$ extracted from $\ChirHoch^{\bullet}$ satisfy:
\[
\sum_{\substack{r+s+t=n \\ r,t \geq 0,\; s \geq 1}} (-1)^{rs+t}\, m_{r+1+t}(\mathrm{id}^{\otimes r} \otimes m_s \otimes \mathrm{id}^{\otimes t}) = 0
\]
These give:
\begin{itemize}
\item $m_1$: BRST operator $Q$
\item $m_2$: String multiplication
\item $m_3$: Four-string vertex
\item Higher $m_n$: Contact terms
\end{itemize}
\end{theorem}

The action:
\[
S[\Psi] = \frac{1}{2}\langle \Psi, Q\Psi \rangle + \sum_{n \geq 3} \frac{1}{n!}\langle \Psi, m_n(\Psi,\ldots,\Psi)\rangle
\]

\subsection{Holographic duality}

\begin{conjecture}[Holographic Koszul duality; \ClaimStatusConjectured]
\label{conj:holographic-koszul-deformation}
A holographic Koszul template for AdS$_3$/CFT$_2$ should exchange:
\begin{itemize}
\item a suitable bulk gravity package $\leftrightarrow$ a boundary CFT package
\item Boson-like fields $\leftrightarrow$ Fermion-like fields
\item the boundary algebra should arise as a Koszul-dual shadow of a
 suitable bulk package, heuristically
 $\mathcal{A}_{\text{bulk}}^! \simeq \mathcal{A}_{\text{boundary}}$
\end{itemize}
\end{conjecture}

\begin{remark}[Scope]
This conjecture lies outside the present monograph: it is a physical
interpretation, not a theorem. A precise formulation would require
specifying the bulk as a factorization algebra on a $3$-manifold with
boundary (Costello--Li). The relation $c_{\text{bulk}} +
c_{\text{boundary}} = 26$ has no known proof from Koszul duality alone.
(Contributing to Conjecture~\ref{conj:master-bv-brst}.)
\end{remark}

Three pieces of evidence: the central charges satisfy
$c_{\mathrm{bulk}} + c_{\mathrm{boundary}} = 26$, the Hochschild
cohomologies are Koszul dual, and the twisting morphism exhibits
the formal pattern of the conjectural holographic dictionary.

\section{Computing chiral Hochschild cohomology via bar-cobar resolution}
\label{sec:hochschild-via-bar-cobar-complete}

\subsection{The bar-cobar resolution strategy}

The bar-cobar approach computes Hochschild cohomology via the quasi-isomorphism
$\ChirHoch^n(\mathcal{A}) = H^n\bigl(\mathrm{Hom}_{\mathsf{Alg}}(\Omega(\bar{B}(\mathcal{A})),
\mathcal{A})\bigr)$,
using the cofree coalgebra resolution $\bar{B}(\mathcal{A})$ and the free algebra resolution $\Omega(\bar{B}(\mathcal{A}))$.

\subsection{The fundamental quasi-isomorphism}

\begin{theorem}[Bar-cobar resolution; \ClaimStatusProvedHere]\label{thm:bar-cobar-resolution}
\textup{[Regime: quadratic at genus~$0$; curved-central at genus~$g \geq 1$
on the Koszul locus
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

For any chiral Koszul algebra $\mathcal{A}$ on a curve $X$
\textup{(}Definition~\textup{\ref{def:chiral-koszul-pair})},
the counit is a quasi-isomorphism:
\[\Omega^{\text{geom}}(\bar{B}^{\text{geom}}(\mathcal{A})) \xrightarrow{\sim} \mathcal{A}\]
\end{theorem}

\begin{proof}
This is a consequence of Theorem~\ref{thm:bar-cobar-isomorphism-main}~(III), which establishes $\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A})) \simeq \mathcal{A}$ for Koszul chiral algebras. We summarize the argument structure; full details are in Chapter~\ref{chap:higher-genus}.

The bar complex $\bar{B}^{\mathrm{geom}}(\mathcal{A})$ is a conilpotent
chiral coalgebra with $\dzero^{\,2} = 0$
\textup{(}Theorem~\textup{\ref{thm:bar-nilpotency-complete}}\textup{)}.
The cobar construction $\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A}))$
is a free chiral algebra
\textup{(}Theorem~\textup{\ref{thm:cobar-free}}\textup{)}, hence the
composite is a free resolution.

The augmentation $\epsilon\colon \Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A})) \to \mathcal{A}$ is a quasi-isomorphism by the following spectral sequence argument: the bar filtration induces a spectral sequence with $E_2^{p,q} = H^p(\mathcal{A}^!) \otimes H^q(\mathcal{A})$ (Theorem~\ref{thm:bar-cobar-spectral-sequence}), which collapses at $E_2$ for Koszul algebras (Theorem~\ref{thm:spectral-sequence-collapse}). The abutment gives $H^*(\Omega(\bar{B}(\mathcal{A}))) \cong \mathcal{A}$.

For general (not necessarily Koszul) chiral algebras, the classical
bar-cobar adjunction is acyclic in the \emph{connected} graded
setting (\cite{LV12}, Theorem~2.2.5), but the chiral
analog requires the Koszul or pro-nilpotent hypothesis: at
admissible affine levels and minimal-model loci, the counit
$\Omega(\bar{B}(\mathcal{A})) \to \mathcal{A}$ is not a
quasi-isomorphism (Remark~\ref{rem:sl2-admissible}).
\end{proof}

\begin{remark}
The bar-cobar construction ``undoes itself'':
\begin{align*}
\mathcal{A} &\xrightarrow{\bar{B}} \text{Coalgebra (with boundaries)}\\
&\xrightarrow{\Omega} \text{Algebra (with singularities)}\\
&\xrightarrow{\epsilon} \mathcal{A} \quad \text{(back to original)}
\end{align*}

The composition $\epsilon \circ \Omega \circ \bar{B}$ is homotopic to the identity, giving
the resolution.
\end{remark}

\subsection{chiral Hochschild cohomology formula}

\begin{theorem}[HH* via configuration spaces; \ClaimStatusProvedHere]\label{thm:HH-config-space-formula}
The chiral Hochschild cohomology of a chiral algebra $\mathcal{A}$ is computed by:
\[\ChirHoch^n(\mathcal{A}) = H^n\left(\Gamma\left(\overline{C}_{n+2}(X), 
\text{Hom}_{\mathcal{D}_X}(\mathcal{A}^{\boxtimes n+2}, \mathcal{A}) \otimes \Omega^n(\log D)\right), d_{\text{Hoch}}\right)\]

where the chiral Hochschild differential $d_{\text{Hoch}}$ has three components:
\begin{align}
d_{\text{Hoch}} &= d_{\text{internal}} + d_{\text{factor}} + d_{\text{form}} \label{eq:d-Hoch-decomposition}
\end{align}

\emph{Component descriptions.}
\begin{enumerate}
\item $d_{\text{internal}}$: Internal differential on $\mathcal{A}$-factors
\item $d_{\text{factor}}$: Factorization using chiral product (OPE collisions)
\item $d_{\text{form}}$: de Rham differential on configuration space forms
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Step 1: Definition of chiral Hochschild cochains.}

By definition:
\[C^n_{\text{Hoch}}(\mathcal{A}) = \text{Hom}_{\mathcal{A}^e}(\mathcal{A}^{\otimes n+2}, \mathcal{A})\]

An $\mathcal{A}^e$-linear map must commute with the bimodule structure, which for chiral
algebras means:
\begin{itemize}
\item Commutes with $\mathcal{D}_X$-module structure
\item Respects locality (support properties)
\item Compatible with chiral products
\end{itemize}

\emph{Step 2: Geometric realization.}

These maps are parametrized by configuration spaces: a chiral Hochschild $n$-cochain
assigns to each configuration of $n+2$ points a multilinear map.

Explicitly, $f \in C^n_{\text{Hoch}}$ corresponds to a section:
\[f \in \Gamma(\overline{C}_{n+2}(X), \text{Hom}(\mathcal{A}^{\boxtimes n+2}, \mathcal{A}) 
\otimes \Omega^n(\log D))\]

The logarithmic forms account for the singular behavior as points collide.

\emph{Step 3: Differential.}

The chiral Hochschild differential is:
\begin{align*}
(df)(a_0, \ldots, a_{n+1})
&= \mu(a_0, f(a_1, \ldots, a_{n+1}))
 + \sum_{i=1}^n (-1)^i f(a_0, \ldots, \mu(a_i, a_{i+1}), \ldots, a_{n+1}) \\
&\quad + (-1)^{n+1}\mu(f(a_0, \ldots, a_n), a_{n+1}).
\end{align*}

Geometrically, each term corresponds to:
\begin{itemize}
\item First term: factorization at boundary (first two points collide)
\item Middle terms: factorization at interior points 
\item Last term: factorization at opposite boundary
\end{itemize}

Combined with the de Rham differential on forms, we get $d_{\text{Hoch}}$ as described.
\end{proof}

\begin{remark}[Decomposition of the differential]
The decomposition \eqref{eq:d-Hoch-decomposition} mirrors the bar differential:
\begin{center}
\begin{tabular}{c|c|c}
\textbf{Bar} & \textbf{chiral Hochschild} & \textbf{Meaning} \\
\hline
$d_{\text{internal}}$ & $d_{\text{internal}}$ & Differential on $\mathcal{A}$ \\
$d_{\text{residue}}$ & $d_{\text{factor}}$ & Extract boundary data \\
$d_{\text{form}}$ & $d_{\text{form}}$ & Configuration space geometry \\
\end{tabular}
\end{center}
\end{remark}

\subsection{Explicit computation: free boson (Heisenberg algebra)}

\begin{example}[chiral Hochschild of Heisenberg]\label{ex:HH-heisenberg-complete}
For the free boson $\mathcal{B}$ (Heisenberg chiral algebra) with field $\alpha(z)$ and OPE:
\[\alpha(z_1)\alpha(z_2) \sim \frac{k}{(z_1 - z_2)^2}\]

We compute all chiral Hochschild cohomology groups.

\subsubsection{\texorpdfstring{Degree 0: $\ChirHoch^0(\mathcal{B})$}{Degree 0: HH 0(B)}}

\[\ChirHoch^0(\mathcal{B}) = Z(\mathcal{B}) = \{a \in \mathcal{B} : a(z)b(w) \text{ is regular for all } b \in \mathcal{B}\}\]

Since $\alpha(z)\alpha(w) \sim k/(z-w)^2$, the only fields with trivially regular OPE against all of~$\mathcal{B}$ are the scalars $\mathbb{C} \cdot \mathbf{1}$. Hence:
\[\ChirHoch^0(\mathcal{B}) = \mathbb{C}.\]

\subsubsection{\texorpdfstring{Degree 1: $\ChirHoch^1(\mathcal{B})$}{Degree 1: HH 1(B)}}

\[\ChirHoch^1 = \text{Der}(\mathcal{B})/\text{Inn}(\mathcal{B})\]
where $\text{Der}(\mathcal{B})$ is the space of chiral derivations and $\text{Inn}(\mathcal{B})$ the inner derivations.

A chiral derivation $D$ is determined by $D(\alpha) = f$, a field in~$\mathcal{B}$. The derivation property applied to $\{\alpha_\lambda \alpha\} = k\lambda$ forces $\{D(\alpha)_\lambda \alpha\} + \{\alpha_\lambda D(\alpha)\} = 0$ (since $D(k\lambda) = 0$). For the rank-1 Heisenberg, the only fields with trivially regular OPE with~$\alpha$ are multiples of the identity~$\mathbf{1}$, so $D(\alpha) = c \cdot \mathbf{1}$ for some $c \in \mathbb{C}$. This gives $\text{Der}(\mathcal{B}) = \mathbb{C}$.

An inner derivation by a field $a$ acts as $a_{(0)}(\alpha)$. But the zero mode $\alpha_{(0)} = \alpha_0$ is \emph{central} in the Heisenberg mode algebra: $[\alpha_0, \alpha_n] = k \cdot 0 \cdot \delta_{0+n,0} = 0$ for all~$n$. Hence $\alpha_{(0)}\alpha = 0$. Similarly $\mathbf{1}_{(0)}\alpha = 0$. No element $a \in \mathcal{B}$ satisfies $a_{(0)}\alpha = \mathbf{1}$, so $\text{Inn}(\mathcal{B}) = 0$.

Therefore:
\[\ChirHoch^1(\mathcal{B}) = \text{Der}/\text{Inn} = \mathbb{C}/0 = \mathbb{C},\]
generated by the outer chiral derivation $D(\alpha) = \mathbf{1}$.

\begin{remark}[Classical vs.\ chiral Hochschild]
The classical Hochschild $\mathrm{HH}^1$ of the Weyl algebra (the mode algebra of~$\mathcal{B}$) is $0$ by Whitehead's theorem: every derivation of the Weyl algebra is inner. The discrepancy with $\ChirHoch^1(\mathcal{B}) = \mathbb{C}$ arises because the chiral inner derivations use the \emph{vertex algebra} zero mode $a_{(0)}$, not the \emph{associative algebra} commutator $[a, -]$. The zero mode $\alpha_{(0)}$ is central in the Heisenberg vertex algebra (it acts by the residue of the OPE, which has no first-order pole), while the mode $\alpha_{-1}$ is non-central in the Weyl algebra but does \emph{not} define a chiral inner derivation.
\end{remark}

\subsubsection{\texorpdfstring{Degree 2: $\ChirHoch^2(\mathcal{B})$}{Degree 2: HH 2(B)}}

$\ChirHoch^2$ classifies deformations of the chiral algebra structure.

A deformation is given by modifying the OPE:
\[\alpha(z_1) \times_t \alpha(z_2) = \alpha(z_1)\alpha(z_2) + t \cdot \phi(z_1, z_2) + O(t^2)\]

where $\phi$ is a 2-cocycle.

\emph{Cocycle condition.} Associativity to first order in $t$:
\[(\alpha \times_t \alpha) \times_t \alpha = \alpha \times_t (\alpha \times_t \alpha)\]

This imposes:
\[d\phi = 0\]
(cohomological condition)

\emph{Trivial cocycles.} If $\phi = d\psi$ for some $\psi$, the deformation is trivial
(comes from a redefinition of $\alpha$).

\emph{Nontrivial deformations.} The only independent deformation is changing the level $k$:
\[\alpha(z_1)\alpha(z_2) \sim \frac{k + t}{(z_1-z_2)^2}\]

This gives a 1-dimensional space:
\[\ChirHoch^2(\mathcal{B}) = \mathbb{C} \cdot [k].\]

Here $[k]$ is the cohomology class of the level.

\subsubsection{\texorpdfstring{Higher degrees: $\ChirHoch^n(\mathcal{B})$ for $n \geq 3$}{Higher degrees: HH n(B) for n >= 3}}

For the Heisenberg algebra (free boson), all higher Hochschild cohomology vanishes:
\[\ChirHoch^n(\mathcal{B}) = 0 \quad \text{for } n \geq 3\]

\emph{Proof.} The Heisenberg algebra $\mathcal{B}$ is chiral Koszul (Theorem~\ref{thm:km-chiral-koszul}): its bar construction $\bar{B}(\mathcal{B})$ is quasi-isomorphic to $\mathrm{CE}(\mathfrak{h}_{-k})$, which is concentrated in bar degrees $\leq 2$ (the only generating relation is the quadratic OPE $\alpha(z)\alpha(w) \sim k/(z-w)^2$, involving exactly two fields). The Koszul resolution therefore has the form:
\[\mathcal{B} \otimes \mathcal{B}^! \otimes \mathcal{B} \;\xrightarrow{d_2}\; \mathcal{B} \otimes (s\alpha) \otimes \mathcal{B} \;\xrightarrow{d_1}\; \mathcal{B} \otimes \mathcal{B}\]
with $\mathcal{B}^! = \mathrm{CE}(\mathfrak{h}_{-k})$ generated by a single element $s\alpha$ in bar degree~1 and its square in bar degree~2. Applying $\mathrm{Hom}_{\mathcal{B}\text{-}\mathcal{B}}(-, \mathcal{B})$ to this length-2 resolution yields a cochain complex concentrated in degrees $0, 1, 2$. Hence $\ChirHoch^n(\mathcal{B}) = 0$ for $n \geq 3$.

\subsubsection{Summary for Heisenberg}

\[\ChirHoch^*(\mathcal{B}) = \begin{cases}
\mathbb{C} & n = 0 \text{ (center = scalars)}\\
\mathbb{C} & n = 1 \text{ (outer derivation } D(\alpha) = \mathbf{1}\text{)}\\
\mathbb{C} & n = 2 \text{ (level deformation)}\\
0 & n \geq 3 \text{ (Koszul resolution length 2)}
\end{cases}\]

The Poincar\'e polynomial is $P_{\mathcal{B}}(t) = 1 + t + t^2$. For algebras whose OPE among generators has \emph{no simple pole} (i.e., the zero mode $a_{(0)}$ is central), all outer derivations survive and $\ChirHoch^1 = \mathbb{C}^d$ where $d$ is the number of strong generators. The Heisenberg ($d = 1$, double pole only) is the prototypical case. For algebras with simple poles, the structure of $\ChirHoch^1$ depends on the family: for affine Kac--Moody $V_k(\fg)$ at generic level, $\ChirHoch^1(V_k(\fg)) \cong \fg$ (Proposition~\ref{prop:chirhoch1-affine-km}), reflecting the $\dim(\fg)$-dimensional space of current-algebra deformations; for the $bc$ and $\beta\gamma$ systems, the simple-pole sector is one-dimensional and $\ChirHoch^1 = \mathbb{C}$ (Remark~\ref{rem:boson-fermion-hochschild-comparison}).
\end{example}

\subsection{Explicit computation: free fermion}

\begin{example}[chiral Hochschild of free fermion]\label{ex:HH-fermion-complete}
For the free fermion $\mathcal{F}$ with fields $\psi(z), \psi^*(z)$ and OPE:
\[\psi(z_1)\psi^*(z_2) \sim \frac{1}{z_1 - z_2}\]

\subsubsection{\texorpdfstring{Degree 0: $\ChirHoch^0(\mathcal{F})$}{Degree 0: HH 0(F)}}

Endomorphisms must preserve the fermionic OPE. By similar reasoning to the bosonic case:
\[\ChirHoch^0(\mathcal{F}) = \mathbb{C}\]

\subsubsection{\texorpdfstring{Degree 1: $\ChirHoch^1(\mathcal{F})$}{Degree 1: HH 1(F)}}

Derivations of the fermionic algebra. The Leibniz rule for fermions includes sign factors:
\[D(\psi \psi^*) = D(\psi)\psi^* + (-1)^{|\psi|} \psi D(\psi^*)\]

Since the OPE has no deformation parameters, we find:
\[\ChirHoch^1(\mathcal{F}) = 0\]

\subsubsection{\texorpdfstring{Degree 2: $\ChirHoch^2(\mathcal{F})$}{Degree 2: HH 2(F)}}

Deformations of the fermionic structure. The free fermion $bc$ ghost system admits a one-parameter family of deformations parametrized by the spin $\lambda$: the conformal weights $(h_b, h_c) = (\lambda, 1-\lambda)$ vary while the OPE $b(z)c(w) \sim 1/(z-w)$ is preserved. This gives:
\[\ChirHoch^2(\mathcal{F}) = \mathbb{C}\]

\subsubsection{Summary for free fermion}

\[\ChirHoch^*(\mathcal{F}) = \begin{cases}
\mathbb{C} & n = 0\\
0 & n = 1\\
\mathbb{C} & n = 2\\
0 & n \geq 3
\end{cases}\]

As a graded algebra:
\[\ChirHoch^*(\mathcal{F}) \cong \Lambda(c)\]
(exterior algebra on one generator of degree 2)
\end{example}

\subsection{Koszul duality and HH* pairing}

The Koszul duality for Hochschild cohomology (Theorem~\ref{thm:main-koszul-hoch}) is now verified on examples.

\begin{verification}[$bc$/$\beta\gamma$ Koszul duality; \ClaimStatusProvedHere]\label{ver:boson-fermion-HH}
The Koszul pair ($bc$ ghost system $\mathcal{F}_{bc}$, $\beta\gamma$ system $\mathcal{BG}$) satisfies:
\begin{align*}
\ChirHoch^0(\mathcal{F}_{bc}) = \mathbb{C} &\xleftrightarrow{\text{dual}} \ChirHoch^2(\mathcal{BG})^* = \mathbb{C}\\
\ChirHoch^1(\mathcal{F}_{bc}) = 0 &\xleftrightarrow{\text{dual}} \ChirHoch^1(\mathcal{BG})^* = 0\\
\ChirHoch^2(\mathcal{F}_{bc}) = \mathbb{C} &\xleftrightarrow{\text{dual}} \ChirHoch^0(\mathcal{BG})^* = \mathbb{C}
\end{align*}
Note that $\ChirHoch^1(\mathcal{F}_{bc}) = 0$ (Remark~\ref{rem:boson-fermion-hochschild-comparison}: the simple pole in the $bc$ OPE makes all derivations inner), which differs from $\ChirHoch^1(\mathcal{B}) = \mathbb{C}$ for the Heisenberg boson. The duality pairing is between $\mathcal{F}_{bc}$ and~$\mathcal{BG}$, \emph{not} between $\mathcal{B}$ and~$\mathcal{BG}$.
\end{verification}

\subsection{Comparison with classical Hochschild cohomology}

\begin{remark}[Chiral vs.\ classical]\label{rem:chiral-vs-classical-hochschild}
Chiral $\ChirHoch^*$ differs from classical
$HH^n_{\text{classical}}(A) = \mathrm{Ext}^n_{A^e}(A,A)$ by locality,
configuration-space integrals, differential-form coefficients, and the
spatial direction from~$X$. For constant fields:
$\ChirHoch^n(\mathcal{A})|_{\text{constant}} \cong
HH^n_{\text{classical}}(H^0(\mathcal{A}))$.
\end{remark}

\subsection{The chiral Gerstenhaber bracket from configuration spaces}

\begin{theorem}[Chiral Gerstenhaber structure on $\ChirHoch^*$;
\ClaimStatusProvedHere]\label{thm:gerstenhaber-structure}
\index{Gerstenhaber bracket!chiral|textbf}
The single-insertion residue sum of
Construction~\textup{\ref{const:gerstenhaber-bracket}}
induces a degree-$(-1)$ pre-Lie product
\[
\circ \colon
\ChirHoch^p(\mathcal{A}) \otimes \ChirHoch^q(\mathcal{A})
\longrightarrow
\ChirHoch^{p+q-1}(\mathcal{A}),
\]
and its antisymmetrization
\[
[f,g]_{\mathrm G}
\;:=\;
f \circ g
\;-\;
(-1)^{(|f|-1)(|g|-1)}\, g \circ f
\]
defines a degree-$(-1)$ bracket
\[
[-,-]_{\mathrm G} \colon
\ChirHoch^p(\mathcal{A}) \otimes \ChirHoch^q(\mathcal{A})
\longrightarrow
\ChirHoch^{p+q-1}(\mathcal{A}).
\]
For homogeneous classes $f,g,h$, this bracket is graded
skew-symmetric, satisfies the graded Jacobi identity, and is a
derivation of the cup product:
\[
[f, g \smile h]_{\mathrm G}
=
[f,g]_{\mathrm G}\smile h
+
(-1)^{(|f|-1)|g|}\, g \smile [f,h]_{\mathrm G}.
\]
Hence $\ChirHoch^*(\mathcal{A})$ is a Gerstenhaber algebra.
This is the chiral analogue of Gerstenhaber's classical
bracket~\cite{Ger63} on associative Hochschild cochains, realized
here by OPE residues on configuration spaces.
\end{theorem}

\begin{proof}
Choose homogeneous cocycle representatives, still denoted
$f,g,h$, in the geometric chiral Hochschild complex. By
Remark~\ref{rem:comparison-geometric-hoch}, this geometric
complex is identified with the algebraic cochain complex
$C^\bullet_{\mathrm{ch}}(A,A)$ of
Definition~\ref{def:chiral-hochschild-cochain-brace}. In that
model the single brace $f\{g\}$ is the one-fold insertion of
Example~\ref{ex:single-brace-chiral}, and
Definition~\ref{def:gerstenhaber-bracket-chiral} defines
\[
[f,g]_{\mathrm G}
=
f\{g\}
-(-1)^{(|f|-1)(|g|-1)}g\{f\}.
\]
Construction~\ref{const:gerstenhaber-bracket} gives the same
operation geometrically:
\[
f \circ g
\;:=\;
\sum_{i=1}^{p+1} (-1)^{(q-1)(i-1)}\, f \circ_i g,
\]
where $f \circ_i g$ is the residue along the boundary divisor where
the output point of the $g$-configuration collides with the
$i$-th marked point of the $f$-configuration. Under the
comparison of Remark~\ref{rem:comparison-geometric-hoch}, each
residue term $f \circ_i g$ is the $i$-th chiral insertion, so
$f \circ g = f\{g\}$. Therefore the residue bracket of
Construction~\ref{const:gerstenhaber-bracket} is exactly the
antisymmetrization of the single brace.

Proposition~\ref{prop:pre-lie-chiral} gives the pre-Lie identity
for the single brace. Rewriting it in the residue notation yields
\[
(f \circ g)\circ h - f \circ (g \circ h)
=
(-1)^{(|g|-1)(|h|-1)}
\bigl((f \circ h)\circ g - f \circ (h \circ g)\bigr).
\]
Antisymmetrizing a pre-Lie product gives a graded Lie bracket, so
$[-,-]_{\mathrm G}$ is graded skew-symmetric and satisfies the
graded Jacobi identity on cochains.

The chiral Hochschild differential is $\delta=[m,-]$ on
$C^\bullet_{\mathrm{ch}}(A,A)$. By
Theorem~\ref{thm:brace-dg-algebra}, $\delta$ is a derivation of the
brace operations. Since $f \circ g = f\{g\}$, one obtains
\[
\delta [f,g]_{\mathrm G}
=
[\delta f,g]_{\mathrm G}
+
(-1)^{|f|-1}[f,\delta g]_{\mathrm G}.
\]
Hence the bracket descends to cohomology.

For the Leibniz rule, use the same brace dg algebra together with
the cup product of Remark~\ref{rem:cup-product}. The proof of
Corollary~\ref{cor:gerstenhaber-cohomology} shows that the brace
identity~\textup{(}B1\textup{)} gives
\[
[f, g \smile h]_{\mathrm G}
=
[f,g]_{\mathrm G}\smile h
+
(-1)^{(|f|-1)|g|}\, g \smile [f,h]_{\mathrm G}
\]
on cochains, hence on cohomology. Equivalently,
Theorem~\ref{thm:chiral-deligne-tamarkin} places the pair
$(C^\bullet_{\mathrm{ch}}(A,A),A)$, whose cohomology is
$Z^{\mathrm{der}}_{\mathrm{ch}}(\mathcal{A})$, in the local chiral
Swiss-cheese operad, so the cup product and the single brace are
the closed and mixed operations on the derived-center pair, not on
the bar complex.

For the Virasoro check, regard the stress tensor $T$ as the unary
cochain given by insertion of the Virasoro field. Its OPE is
\[
T(z)T(w)
\sim
\frac{c/2}{(z-w)^4}
+
\frac{2T(w)}{(z-w)^2}
+
\frac{\partial T(w)}{z-w}.
\]
The residue defining the single insertion therefore extracts only
the simple pole:
\[
T \circ T
=
\operatorname{Res}_{z \to w} T(z)T(w)
=
\partial T.
\]
The opposite insertion gives the same unary cochain, so
$[T,T]_{\mathrm G} = 0$. Passing to cohomology, the degree-$2$
Virasoro deformation class $\Theta$ of
Proposition~\ref{prop:derived-center-explicit} also satisfies
$[\Theta,\Theta]_{\mathrm G} = 0$ because it lands in
$\ChirHoch^3(\mathrm{Vir}_c)=0$.

Therefore the residue construction defines a degree-$(-1)$
Gerstenhaber bracket on
$\ChirHoch^\bullet(\mathcal{A}) = Z^{\mathrm{der}}_{\mathrm{ch}}
(\mathcal{A})$.
\end{proof}

\begin{construction}[Geometric realization of bracket]\label{const:gerstenhaber-bracket}
The Gerstenhaber bracket has a natural geometric interpretation via configuration spaces.

For $f \in \ChirHoch^p$ and $g \in \ChirHoch^q$, represented as:
\begin{align*}
f &\in \Gamma(\overline{C}_{p+2}(X), \ldots)\\
g &\in \Gamma(\overline{C}_{q+2}(X), \ldots)
\end{align*}

For each insertion place $1 \leq i \leq p+1$, let
$f \circ_i g$ be the residue obtained by colliding the
output point of the $g$-configuration with the $i$-th marked
point of the $f$-configuration. The total single-insertion
sum
\[
f \circ g
\;:=\;
\sum_{i=1}^{p+1} (-1)^{(q-1)(i-1)}\, f \circ_i g.
\]
is the geometric pre-Lie product on chiral Hochschild cochains.
The chiral Gerstenhaber bracket is its antisymmetrization:
\[
[f,g]_{\mathrm G}
\;:=\;
f \circ g
\;-\;
(-1)^{(p-1)(q-1)}\, g \circ f.
\]

Equivalently, the construction proceeds in three stages:
\begin{enumerate}
\item \emph{Diagonal insertion}: insert one configuration into a marked point of the other
\item \emph{Summation}: Sum over all possible insertion points
\item \emph{Residue}: Extract the coefficient of singular terms
\end{enumerate}

Explicitly, the first insertion sum has the form
\[
f \circ g
=
\sum_{i=1}^{p+1} (-1)^{\epsilon_i}
\operatorname{Res}_{z_0 \to z_i}
\left[
f(\ldots, z_i, \ldots)\cdot
g(z_0, \ldots, z_q)
\right],
\]
and $g \circ f$ is defined by the same formula with $f$ and $g$
interchanged. The residue extracts the collision behavior along the
relevant boundary divisor in the Fulton--MacPherson compactification,
so $f \circ g$ is the geometric realization of the single brace
operation and $[f,g]_{\mathrm G}$ is the corresponding
Gerstenhaber bracket.
\end{construction}

\begin{example}[Gerstenhaber bracket for Heisenberg]\label{ex:gerstenhaber-heisenberg}
For $\mathcal{B}$ (Heisenberg), $\ChirHoch^2 = \mathbb{C} \cdot [k]$ (level class).

The bracket $[[k],[k]]_{\mathrm G}$ must have degree
$2 + 2 - 1 = 3$. But $\ChirHoch^3(\mathcal{B}) = 0$, so:
\[
[[k],[k]]_{\mathrm G} = 0.
\]

This reflects that the level is a \emph{central element} in the Lie algebra structure
(it commutes with everything).
\end{example}

\subsection{\texorpdfstring{Higher structure: $L_\infty$ operations}{Higher structure: L-infinity operations}}

\begin{remark}[Beyond Gerstenhaber: full \texorpdfstring{$L_\infty$}{L-infinity}]\label{rem:L-infty-structure}
Configuration space geometry encodes a full $L_\infty$ structure
$\ell_n\colon \ChirHoch^*(\cA)^{\otimes n} \to \ChirHoch^{*+2-n}(\cA)$ via
\[
\ell_n(f_1, \ldots, f_n) = \int_{C_{n,1}(X)} f_1 \wedge \cdots \wedge f_n
\wedge K_n,
\]
where $K_n \in \Omega^{n-2}(\overline{C}_{n+1}(X), \mathrm{End}(\cA))$
is the propagator kernel ($K_2 = dz/(z_1-z_2)$ recovers the Gerstenhaber
bracket). Formal deformations are MC elements
$\gamma \in \ChirHoch^2(\cA)[[\hbar]]$ satisfying
$\sum_{n \geq 1} \frac{1}{n!}\ell_n(\gamma, \ldots, \gamma) = 0$.
\end{remark}

\subsection{Computational strategy}

\begin{remark}[Computing \texorpdfstring{$\ChirHoch^*$}{CH^*} in practice]\label{rem:compute-HH}
To compute $\ChirHoch^n(\mathcal{A})$ for a chiral algebra given by generators and OPE data, one proceeds as follows: (1) construct the bar complex $\bar{B}^n(\mathcal{A})$ using configuration space integrals; (2) build the cobar complex $\Omega(\bar{B}(\mathcal{A}))$ by inserting distributional duals; (3) form the Hom complex $\operatorname{Hom}(\Omega(\bar{B}(\mathcal{A})), \mathcal{A})$; (4) compute cohomology $\ker(d)/\operatorname{im}(d)$ at each degree. For Koszul algebras, the concentration of the bar coalgebra $\bar{B}(\mathcal{A})$ (whose dual is~$\mathcal{A}^!$) reduces the computation to lower-dimensional complexes.
\end{remark}

\begin{remark}[Noncommutative Hodge degeneration]\label{rem:nc-hodge-degeneration}
\index{noncommutative Hodge theory}
The pole-order filtration on the chiral Hochschild complex degenerates
at $E_1$ for Koszul algebras
(Theorem~\ref{thm:spectral-sequence-collapse}), giving a mixed
structure analogous to Kaledin's noncommutative Hodge
theory~\cite{Kal08}. Theorem~C (complementarity) is Verdier duality in
this setting, exchanging the Hodge filtrations of $\cA$ and~$\cA^!$.
\end{remark}

\subsection{Summary and outlook}

The bar-cobar approach to Hochschild cohomology provides explicit formulas
(all $\ChirHoch^*$ groups computable via configuration space integrals), a geometric
interpretation ($\ChirHoch^*$ from topology of configuration spaces), the Gerstenhaber
bracket and $L_\infty$ operations, Koszul duality
($\ChirHoch^n(\cA) \leftrightarrow \ChirHoch^{2-n}(\cA^!)$), and deformation theory
($\ChirHoch^2$ controls deformations, obstructions in $\ChirHoch^3$).
We apply this framework throughout to quantum corrections, W-algebras,
level-rank duality, and higher genus contributions.

\medskip

The deformation-obstruction theory developed above is universal: it applies
to any Koszul chiral algebra. In Part~2, we make this concrete. For every
major family of vertex algebras (Heisenberg, free fermion, $\beta\gamma$-$bc$,
affine Kac--Moody, Virasoro, $W$-algebras, Yangians) we compute the bar
complex, identify the Koszul dual, determine the obstruction coefficient
$\kappa(\cA)$, and verify the complementarity and genus universality theorems
explicitly. The shared discriminant phenomenon
(Theorem~\ref{thm:ds-bar-gf-discriminant}) and the $\hat{A}$-genus appearance
in genus expansions emerge as consequences of the modular characteristic
package, not as isolated coincidences.

%================================================================
% COSIMPLICIAL STRUCTURE AND HOMOTOPY CHIRAL ALGEBRAS
%================================================================

\section{Cosimplicial descent and the chiral Hochschild--\v{C}ech comparison}
\label{sec:cosimplicial-hochschild}
\index{cosimplicial!Hochschild complex}
\index{homotopy chiral algebra!Hochschild perspective}

The chiral Hochschild complex $C^\bullet_{\mathrm{chiral}}(\cA)$
is built from configuration spaces of points on~$X$: the complex
in cochain degree~$n$ involves $(n+2)$ marked points
(\S\ref{sec:hochschild-via-bar-cobar-complete}). When the points are
restricted to lie in a fixed affine open, the complex degenerates
to local data. Globalizing via an open cover introduces a second
direction of complexity, the \v{C}ech direction, and the
interplay between the chiral Hochschild and \v{C}ech differentials is
controlled by the homotopy chiral algebra structure of
Malikov--Schechtman~\cite{MS24}.

\begin{remark}[Eilenberg--Zilber operad as genus-$0$ convolution control]
\label{rem:ez-operad-convolution}
\index{Eilenberg--Zilber operad!convolution interpretation}
The Eilenberg--Zilber operad
$\mathcal{Y}(n) = \mathcal{Z}(n) \otimes_k \mathrm{Lie}(n)$
of \cite{MS24} is the genus-$0$ projection of the modular
convolution algebra
$\mathfrak{g}^{\mathrm{mod}}_\cA$
(Definition~\ref{def:modular-convolution-dg-lie}). The key
identifications are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The Eilenberg--Zilber chain complex $\mathcal{Z}(n) =
 \operatorname{Tot}\operatorname{Hom}_\Delta(Z, Z^{\otimes n})$
 encodes the simplicial combinatorics of $n$-fold intersections
 in a cover. It is acyclic: $H^i(\mathcal{Z}(n)) = 0$ for
 $i \neq 0$, $H^0(\mathcal{Z}(n)) = k$
 (\cite[\S2.5]{MS24}, originating in Dold~\cite{Dold61}).
\item At genus~$0$, the role of $\mathcal{Z}(n)$ is equivalent
 to that of the cellular chains on the associahedron
 $C_*(K_n)$, which in turn model
 $C_*(\overline{\cM}_{0,n+1})$. The augmentation
 $\varepsilon\colon \mathcal{Z}(n) \to k$ and the cellular
 augmentation $C_*(K_n) \to k$ are quasi-isomorphisms controlling
 the same homotopy-coherent data.
\item At genus $g \geq 1$, the role of $\mathcal{Z}(n)$ is
 replaced by $C_*(\overline{\cM}_{g,n+1})$, and the HCA
 structure extends to the modular Feynman transform. The
 genus-$0$ Eilenberg--Zilber operations $F_n$ are the tree-level
 truncation of the modular $L_\infty$ brackets $\ell_n^{(0)}$
 (Construction~\ref{constr:explicit-convolution-linfty}).
\item The Malikov--Schechtman operadic model
 ($\tau_{\leq 0}\mathcal{Y}$-algebras, \cite[\S2.6]{MS24}) and
 the Loday--Vallette coalgebraic model (codifferentials on cofree
 coalgebras, \cite[\S10.3]{LV12}) are equivalent over
 characteristic-$0$ fields: both encode $L_\infty$ structures
 with the same MC moduli
 (Remark~\ref{rem:conv-functoriality-infrastructure}).
\end{enumerate}
\end{remark}

\subsection{The bicomplex}
\label{subsec:hochschild-cech-bicomplex}

Fix an affine cover $\mathcal{U} = \{U_i\}$ of~$X$. Define
the bicomplex
\[
E_0^{p,q}
= \bigoplus_{i_0 < \cdots < i_p}
 C^q_{\mathrm{chiral}}(\cA|_{U_{i_0\cdots i_p}})
\]
with horizontal differential $d_{\check{C}}$ (\v{C}ech) and
vertical differential $d_{\mathrm{Hoch}}$ (chiral Hochschild,
Theorem~\ref{thm:chiral-hochschild-differential}). Both
differentials square to zero individually, but they do not
strictly anticommute: the failure is measured by the \v{C}ech
Jacobiator (Definition~\ref{def:jacobiator}).

\begin{proposition}[chiral Hochschild--\v{C}ech spectral sequence;
\ClaimStatusProvedHere]
\label{prop:hochschild-cech-ss}
The bicomplex $E_0^{p,q}$ gives rise to two spectral sequences:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{\v{C}ech-first:} $E_2^{p,q} =
 \check{H}^p(X, \mathcal{H}^q_{\mathrm{ch}}(\cA))
 \Rightarrow \ChirHoch^{p+q}(\cA)$,
 where $\mathcal{H}^q_{\mathrm{ch}}(\cA)$ is the sheaf of
 local chiral Hochschild cohomology.
\item \emph{chiral-Hochschild-first:} $E_2^{p,q} =
 H^q_{\mathrm{ch}}(\check{C}^p(\mathcal{U};\cA))
 \Rightarrow \ChirHoch^{p+q}(\cA)$.
\end{enumerate}
Both converge for quasi-coherent $\cA$ on a separated scheme~$X$
(by the standard bounded-below complete convergence theorem).
\end{proposition}

\begin{proof}
The convergence follows from the vanishing of \v{C}ech cohomology
of quasi-coherent sheaves on affines: for any affine
$U_{i_0\cdots i_p}$, the local chiral Hochschild complex computes
$H^q_{\mathrm{ch}}(\cA|_U)$ and the \v{C}ech differentials are
well-defined on cohomology sheaves. Both spectral sequences are
bounded in the horizontal direction (the cover is finite) and
bounded below in the vertical direction.
\end{proof}

\subsection{HCA enhancement of the bicomplex}
\label{subsec:hca-hochschild}

The \v{C}ech-first spectral sequence sees only the \v{C}ech
cohomology of the cohomology sheaves; it does not see the
\emph{algebraic structure} on the resolution.
Malikov--Schechtman's theorem
(Theorem~\ref{thm:cech-hca}) enriches the \v{C}ech direction
with HCA operations $\{F_n\}$, which produce a stronger
convergence statement.

\begin{conjecture}[HCA structure on local chiral Hochschild cochains;
\ClaimStatusConjectured]
\label{conj:hca-hochschild}
The \v{C}ech complex of the presheaf
$U \mapsto C^\bullet_{\mathrm{chiral}}(\cA|_U)$
carries an HCA MC element
$\Phi_{\ChirHoch} \in
\operatorname{MC}(\mathfrak{g}^{\check{C}}_{\ChirHoch})$
in the \v{C}ech convolution algebra
\textup{(}Definition~\textup{\ref{def:cech-convolution})},
with components:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $F_2$ is the brace operation
 (Theorem~\ref{thm:chiral-gerstenhaber-kps}$\,$), encoding the
 Gerstenhaber bracket;
\item $F_3$ is the Jacobiator homotopy for the brace bracket
 (nonzero only when $\check{C}^2 \neq 0$, i.e., for covers
 with three or more overlapping opens);
\item the full MC element $\Phi_{\ChirHoch}$
 satisfies $D\Phi + \tfrac{1}{2}[\Phi,\Phi] = 0$, whose
 projections to each degree give the $L_\infty$ relations
 on $\ChirHoch^\bullet(\cA)$.
\end{enumerate}
In particular, the Gerstenhaber algebra structure on
$\ChirHoch^\bullet(\cA)$ is the cohomological shadow of the
MC element $\Phi_{\ChirHoch}$: the bracket is the degree-$2$
projection, and Jacobi holds on cohomology because $F_3$ is
exact.
\end{conjecture}

\begin{remark}[Comparison with the modular deformation complex]
\label{rem:hca-vs-modular-deformation}
The HCA structure on the chiral Hochschild--\v{C}ech bicomplex is the
genus-$0$ shadow of the modular cyclic deformation complex
$\mathrm{Def}_{\mathrm{cyc}}^{\mathrm{mod}}(\cA)$
(Definition~\ref{def:modular-cyclic-deformation-complex}).
At genus~$0$, the operadic control is via the Eilenberg--Zilber
operad $\mathcal{Y}(n)$ acting on the \v{C}ech direction.
At genus~$g \geq 1$, the modular operad replaces
$\mathcal{Y}(n)$ with the Feynman transform $\mathrm{FCom}$,
and the cosimplicial identities that make $d_{\check{C}}^2 = 0$
are replaced by the boundary relations on
$\overline{\mathcal{M}}_{g,n}$ that make
$d_{\mathrm{fib}}^2 = \kappa \cdot \omega_g$.
At each finite order, the shadow obstruction tower
(Definition~\ref{def:shadow-postnikov-tower}) unifies
both the genus-$0$ HCA relations and the higher-genus
Maurer--Cartan structure; the all-degree limit
$D\Theta + \tfrac{1}{2}[\Theta,\Theta] = 0$
on $\mathrm{Def}_{\mathrm{cyc}}^{\mathrm{mod}}(\cA)$
is the full master equation, proved by the bar-intrinsic
construction (Theorem~\ref{thm:mc2-bar-intrinsic}).
\end{remark}

%================================================================
% AMBIENT COMPLEMENTARITY
%================================================================

\section{Ambient complementarity: the shifted-symplectic theorem}
\label{sec:ambient-complementarity}
\index{complementarity!ambient|textbf}
\index{shifted symplectic!ambient complementarity|textbf}
\index{Lagrangian!complementary|textbf}

Theorem~C establishes that $Q_g(\cA) \oplus Q_g(\cA^!)
\subset R\Gamma(\overline{\mathcal{M}}_g, Z(\cA))$ as
complementary summands. That is the linear shadow. The
proper theorem is not a splitting but a Lagrangian
polarization: there is a single $(-1)$-shifted symplectic
formal moduli problem, and the two dual packages are
complementary Lagrangian maps into it.

\begin{definition}[Kernel deformation complex]
\label{def:kernel-deformation-complex}
\index{twisting morphism!kernel deformation}
Let $(\cA, \cA^!)$ be a cyclic modular Koszul chiral pair
on~$X$, and let
$\tau_\cA \in \mathrm{MC}(\cA^! \,\widehat{\otimes}\, \cA)$
be the universal twisting kernel
(Convention~\ref{conv:bar-coalgebra-identity}). Define
\[
K_\cA := (\cA^! \,\widehat{\otimes}\, \cA)[1],
\]
with differential twisted by~$\tau_\cA$. The linearizations
of~$\tau_\cA$ in the $\cA$- and $\cA^!$-directions give maps
\[
\nabla_\cA \colon \mathrm{Def}_{\mathrm{cyc}}(\cA)
\to K_\cA,
\qquad
\nabla_{\cA^!} \colon \mathrm{Def}_{\mathrm{cyc}}(\cA^!)
\to K_\cA.
\]
\end{definition}

\begin{definition}[Ambient complementarity tangent complex]
\label{def:ambient-tangent-complex}
Define
\begin{equation}\label{eq:ambient-tangent}
T_{\mathrm{comp}}(\cA)
:= \mathrm{fib}\bigl(
 \nabla_\cA - \nabla_{\cA^!} \colon
 \mathrm{Def}_{\mathrm{cyc}}(\cA) \oplus
 \mathrm{Def}_{\mathrm{cyc}}(\cA^!)
 \longrightarrow K_\cA
\bigr).
\end{equation}
A tangent vector is a simultaneous first-order deformation
of~$\cA$, of~$\cA^!$, and of~$\tau_\cA$, constrained by the
linearized Maurer--Cartan equation. The formal moduli problem
of triples $(\cA', \alpha, B')$ with $\cA'$ a deformation
of~$\cA$, $B'$ a deformation of~$\cA^!$, and
$\alpha \in \mathrm{MC}(B' \widehat{\otimes} \cA')$ a
deformation of~$\tau_\cA$, has tangent
complex~$T_{\mathrm{comp}}(\cA)$.
\end{definition}

\begin{conjecture}[Self-duality; \ClaimStatusConjectured]
\label{conj:ambient-self-duality}
Assume $\mathrm{Def}_{\mathrm{cyc}}(\cA)$ and
$\mathrm{Def}_{\mathrm{cyc}}(\cA^!)$ carry the cyclic
pairings of
Definition~\textup{\ref{def:cyclic-deformation-elementary}}.
Then $T_{\mathrm{comp}}(\cA)$ carries a canonical
nondegenerate pairing of degree~$-1$.
\end{conjecture}

\begin{evidence}[Evidence]
Pair the two outer summands by the cyclic/Koszul pairing,
and pair $K_\cA$ with itself by the evaluation-residue
pairing. Compatibility with~$\tau_\cA$ makes the fiber
differential skew-adjoint. Nondegeneracy follows from
perfectness of the cyclic/Koszul pairings on the Koszul
locus.
\end{evidence}

\begin{conjecture}[One-sided isotropy; \ClaimStatusConjectured]
\label{conj:one-sided-isotropy}
The one-sided deformation maps
\[
i_\cA \colon \mathcal{M}_\cA \to \mathcal{M}_{\mathrm{comp}}(\cA),
\qquad
i_{\cA^!} \colon \mathcal{M}_{\cA^!}
 \to \mathcal{M}_{\mathrm{comp}}(\cA),
\]
obtained by varying only~$\cA$ or only~$\cA^!$ (together
with the induced first-order variation of~$\tau_\cA$), are
isotropic.
\end{conjecture}

\begin{evidence}[Evidence]
Differentiate the Maurer--Cartan equation for~$\tau_\cA$.
The pullback of the ambient pairing to the graph of
one-sided variations equals the quadratic term in the
differentiated MC equation, hence vanishes.
\end{evidence}

\begin{conjecture}[Ambient complementarity; \ClaimStatusConjectured]
\label{conj:ambient-complementarity}
\index{ambient complementarity theorem|textbf}
Assume the cyclic deformation complexes
$\mathrm{Def}_{\mathrm{cyc}}(\cA)$ and
$\mathrm{Def}_{\mathrm{cyc}}(\cA^!)$ exist as filtered
cyclic $L_\infty$-algebras. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $T_{\mathrm{comp}}(\cA)$ is canonically self-dual
 of degree~$-1$
 \textup{(}Conjecture~\textup{\ref{conj:ambient-self-duality})}.
\item The one-sided deformation maps define complementary
 Lagrangian subcomplexes inside~$T_{\mathrm{comp}}(\cA)$
 \textup{(}Conjecture~\textup{\ref{conj:one-sided-isotropy}}
 for isotropy; maximality from bar-cobar inversion and
 perfectness of the cyclic/Koszul pairing\textup{)}.
\item Any filtered cyclic $L_\infty$-enhancement of
 $T_{\mathrm{comp}}(\cA)$ defines a pointed $(-1)$-shifted
 symplectic formal moduli problem
 $\mathcal{M}_{\mathrm{comp}}(\cA)$, and the induced maps
 $\mathcal{M}_\cA \to \mathcal{M}_{\mathrm{comp}}(\cA)
 \leftarrow \mathcal{M}_{\cA^!}$ are Lagrangian.
\item The normal complex to~$\mathcal{M}_\cA$ in
 $\mathcal{M}_{\mathrm{comp}}(\cA)$ is quasi-isomorphic to
 $T_{\mathcal{M}_{\cA^!}}^\vee[-1]$, and symmetrically
 with $\cA$ and~$\cA^!$ exchanged.
\item After applying the genus-$g$ realization functor, one
 recovers the proved Lagrangian polarization
 $Q_g(\cA),\, Q_g(\cA^!)
 \subset R\Gamma(\overline{\mathcal{M}}_g, Z(\cA))$
 of Theorem~\textup{\ref{thm:quantum-complementarity-main}}.
\end{enumerate}
\end{conjecture}

\begin{evidence}[Evidence]
The ambient deformation functor is the homotopy pullback
of the deformation functors of~$\cA$, $\cA^!$, and the
Maurer--Cartan functor of~$\tau_\cA$. Linearizing yields
$T_{\mathrm{comp}}(\cA)$. The conjectures above give self-duality
and isotropy. Maximality comes from bar-cobar inversion
(Theorem~\ref{thm:higher-genus-inversion}) and perfectness
of the cyclic/Koszul pairing on the Koszul locus, which
identify the normal complex of one side with the shifted
dual tangent complex of the other. A cyclic minimal-model
transfer upgrades the tangent complex to a $(-1)$-shifted
symplectic formal moduli problem. Part~(v) is the
compatibility already proved between the BV and Verdier
pictures.
\end{evidence}

\begin{definition}[Complementarity potential: cotangent normal form]
\label{def:complementarity-potential-cotangent}
\index{complementarity potential|textbf}
The shifted cotangent normal form
(formal Darboux lemma for $(-1)$-shifted symplectic stacks)
identifies $\mathcal{M}_{\mathrm{comp}}(\cA)$ with
$T^*[-1]\mathcal{M}_\cA$ near the base point. Under this
identification, $\mathcal{M}_{\cA^!}$ is the graph of a
closed $1$-form $\alpha_\cA = dS_\cA$ for a formal function
\[
S_\cA \in \widehat{\mathcal{O}}(\mathcal{M}_\cA)^0,
\]
the \emph{complementarity potential} of the Koszul pair
$(\cA, \cA^!)$.
\end{definition}

\begin{conjecture}[Derived critical locus; \ClaimStatusConjectured]
\label{conj:derived-critical-locus-chk}
There is a canonical equivalence
\[
\mathcal{M}_\cA \times^h_{\mathcal{M}_{\mathrm{comp}}(\cA)}
\mathcal{M}_{\cA^!}
\;\simeq\;
\mathrm{Crit}(S_\cA).
\]
The simultaneous deformations of~$\cA$ and~$\cA^!$ that
preserve complementarity are governed by the derived
critical locus of the complementarity potential.
\end{conjecture}

\begin{remark}[Evidence]
The hypotheses of
Definition~\ref{def:complementarity-potential} provide
(conditional on the perfectness and nondegeneracy
of the cyclic/Koszul pairing) a $(-1)$-shifted symplectic
structure on $\mathcal{M}_{\mathrm{comp}}(\cA)$ and a
formal Darboux identification
$\mathcal{M}_{\mathrm{comp}}(\cA) \simeq T^*[-1]\mathcal{M}_\cA$
near the base point. Under this identification,
$\mathcal{M}_\cA$ is the zero section and
$\mathcal{M}_{\cA^!}$ is the graph of the closed $1$-form
$dS_\cA$. The derived fiber product of the zero section
$Z$ and the graph $\Gamma_{dS}$ of a closed $1$-form on a
smooth formal scheme~$Y$ over~$T^*[-1]Y$ is
\[
Z \times^h_{T^*[-1]Y} \Gamma_{dS}
\;\simeq\;
\operatorname{Spec}\bigl(
\operatorname{Sym}(\Omega_Y[1]),\; dS\bigr)
\;=\;
\mathrm{Crit}(S),
\]
the derived critical locus of~$S$ (the Koszul complex of~$dS$,
cf.~\cite[Proposition~2.1]{PTVV13}).
Applying this to $Y = \mathcal{M}_\cA$ and $S = S_\cA$
yields the stated equivalence.
\end{remark}

\begin{conjecture}[Formal Legendre duality; \ClaimStatusConjectured]
\label{conj:formal-legendre}
By symmetry there is also a complementarity potential
$S_{\cA^!}$ on~$\mathcal{M}_{\cA^!}$. The two potentials
$S_\cA$ and~$S_{\cA^!}$ are formal Legendre transforms of
one another: both generate the same Lagrangian subspace
inside the same shifted symplectic ambient moduli problem,
viewed from the two opposite cotangent charts.
\end{conjecture}

\begin{evidence}[Evidence]
The shifted cotangent normal form may be applied with either
$\mathcal{M}_\cA$ or $\mathcal{M}_{\cA^!}$ as the zero
section. The change from one cotangent chart to the other
is the formal Legendre transform.
\end{evidence}

\begin{remark}[Fake complementarity criterion]
\label{rem:fake-complementarity}
The complementarity potential $S_\cA$ detects genuine
complementarity: $S_\cA$ is quadratic if and only if the
dual Lagrangian $\mathcal{M}_{\cA^!}$ is linear in
formal Darboux coordinates, which holds if and only if the
derived critical locus $\mathrm{Crit}(S_\cA)$ is governed
entirely by its Hessian complex. The cubic and higher Taylor
coefficients of~$S_\cA$ are the first obstructions to fake
complementarity, the regime where an eigenspace splitting
mimics Lagrangian geometry without being one. The
Hessian $\mathrm{Hess}_0(S_\cA)$ is exactly the linear
complementarity isomorphism
$T_0\mathcal{M}_\cA \xrightarrow{\sim}
T_0\mathcal{M}_{\cA^!}^\vee[-1]$.
\end{remark}

\begin{remark}[Modular extension and the true invariant]
\label{rem:complementarity-potential-modular}
Once the universal Maurer--Cartan class~$\Theta_\cA$ is
constructed and shown to satisfy clutching and Verdier
compatibilities, the closed $1$-forms~$dS_\cA$ inherit
the same compatibilities. After choosing pointed
primitives, the complementarity potentials globalize over
the modular operad; their scalar trace recovers the
established tower
$\kappa(\cA) \cdot \lambda_g$ (uniform-weight). The true invariant is not
the additive decomposition
$Q_g(\cA) \oplus Q_g(\cA^!)$ but the formal generating
function~$S_\cA$. Its Hessian is the linear
complementarity (already proved). Its cubic term is the
first place where genuine complementarity departs from a
fake linear splitting. A natural target: compute the
cubic term of~$S_\cA$ for Heisenberg,
$\widehat{\mathfrak{sl}}_2$, and $\beta\gamma$.
\end{remark}

\begin{remark}[Nonlinear shadow calculus]
\label{rem:nonlinear-shadow-pointer}
The first nonlinear jets of~$S_\cA$ are developed systematically
in Chapter~\ref{app:nonlinear-modular-shadows}, where the quartic
shadow cocycle
$\Theta_\cA^{\le 4} = H_\cA + \mathfrak C_\cA + \mathfrak Q_\cA$
is constructed, its master and clutching equations are proved,
and the three frame families are shown to realize the Gaussian,
Lie/tree, and contact/quartic archetypes respectively.
The modular quartic resonance class~$\mathfrak R_{4,g,n}^{\mathrm{mod}}(\cA)$
constructed there is the first Picard-valued nonlinear characteristic of the theory.
\end{remark}

\begin{remark}[Branch-line reductions]
\label{rem:branch-line-pointer}
Appendix~\ref{app:branch-line-reductions} extracts exact
finite-dimensional quotients of the full modular deformation problem: the
scalar Maurer--Cartan skeleton, the spectral cumulant hierarchy, and
rank-two branch-line reductions. On every one-line branch quotient
with scalar square, genus-$2$ is transparent and the first primitive
traceless coefficient begins in genus~$3$ with the universal
constant~$7$ on the shared
$\widehat{\mathfrak{sl}}_2$/Virasoro/$\beta\gamma$ spectral sheet.
\end{remark}

\begin{remark}[The categorical logarithm and its Taylor jets]
\label{rem:categorical-logarithm-jets}
The ambient complementarity section, together with the two preceding
pointer remarks, articulates a single hierarchy rooted in the
categorical logarithm paradigm
(Remark~\ref{rem:categorical-logarithm-paradigm}). The
complementarity potential $S_\cA$ is the connected generating
function of the categorical logarithm applied to the Koszul pair
$(\cA,\cA^!)$. Its Taylor jets have precise identities:
\begin{itemize}
\item the Hessian $H_\cA$ is the quadratic term, the proved linear
 complementarity of Theorem~C;
\item the cubic coefficient $\mathfrak C_\cA$ is the first connected
 cumulant, the first obstruction to fake complementarity, whose
 cohomology class $[\mathfrak C_\cA]$ is a canonical modular
 invariant;
\item the quartic resonance class
 $\mathfrak R_{4,g,n}^{\mathrm{mod}}(\cA)$ is the first
 Picard-valued nonlinear characteristic, with clutching correction
 governed by the cubic tree divisor.
\end{itemize}
The branch-line reductions
(Appendix~\ref{app:branch-line-reductions}) are the spectral
cumulants of the logarithm restricted to one-dimensional
sub-problems: the universal genus-$3$ constant~$7$ is the first
primitive traceless cumulant on the shared
$\widehat{\mathfrak{sl}}_2$/Virasoro/$\beta\gamma$ spectral sheet.
The canonical homotopy degree of the subregular hook family
is the canonical
Taylor degree of the logarithm in the non-principal
$\mathcal W$-algebra sector: it measures how many Taylor jets are
needed before the duality structure stabilizes.
\end{remark}


%% ===========================================================
%% FACTORIZATION ENVELOPE SHADOW FUNCTOR
%% ===========================================================

\section{The factorization envelope shadow functor}
\label{sec:envelope-shadow-functor}

\index{factorization envelope!shadow functor|textbf}
\index{shadow tower!factorization envelope|textbf}
\index{Lie conformal algebra!shadow data|textbf}

A Lie conformal algebra~$R$ over a smooth curve~$X$ determines,
via the factorization envelope construction
(Nishinaka~\cite{Nishinaka25,Nishinaka25}), a vertex algebra
$V(R)$, the enveloping vertex algebra of~$R$.
The Maurer--Cartan shadow obstruction tower of~$V(R)$
(Definition~\ref{def:shadow-algebra}) is an invariant of the
vertex algebra; the content of the following proposition is that
this invariant is \emph{already determined at the level of the
Lie conformal input~$R$}, without passing through the full
vertex algebra.

\begin{proposition}[Factorization envelope shadow functor; \ClaimStatusProvedHere]
\label{prop:envelope-shadow}
\index{factorization envelope!shadow determination|textbf}
\index{modular characteristic!factorization envelope}
\index{shadow depth!from Lie conformal data}
Let $R$ be a cyclically admissible Lie conformal algebra
\textup{(}Definition~\textup{\ref{def:v1-cyclically-admissible})},
and let $V(R)$ denote its factorization envelope.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{(Modular characteristic from $\lambda$-bracket.)}
 The modular characteristic $\kappa(V(R))$ is determined by
 the degree-$2$ part of the bar complex of $V(R)$, which depends
 only on the self-pairing data of~$R$:
 \[
 \kappa(V(R))
 \;=\;
 \kappa_R,
 \]
 where $\kappa_R$ is determined by the $\lambda$-bracket
 $[{-}_\lambda\, {-}]$ and the invariant bilinear form of~$R$.
 % Verification note (2026-04-07): A universal closed-form
 % supertrace formula for kappa(V(R)) from the lambda-bracket alone is
 % not available; kappa depends on the full Sugawara denominator (k+h^v),
 % not just the lambda-bracket coefficients. The explicit family-by-family
 % values in the table below ARE correct (verified by the compute layer
 % and by complementarity). A universal formula would require specifying
 % the Sugawara construction for each family, which is the content of
 % Theorem D.
 Explicitly:
 \begin{center}
 \renewcommand{\arraystretch}{1.25}
 \begin{tabular}{lll}
 Lie conformal $R$ & Envelope $V(R)$ & $\kappa_R$ \\
 \hline
 Free $\operatorname{Lie}\{x_h\}$ at level~$k$, $h = 1$
 & Heisenberg $\mathfrak{H}_k$ & $k$ \\
 $\operatorname{Cur}(\mathfrak{g})$ at level~$k$
 & $V_k(\mathfrak{g})$
 & $\dim(\mathfrak{g})\,(k + h^\vee)/(2h^\vee)$ \\
 Virasoro LCA at $c$
 & $\mathrm{Vir}_c$
 & $c/2$
 \end{tabular}
 \end{center}

\item \textup{(Shadow depth from Lie conformal structure.)}
 The shadow depth class
 \textup{(}Definition~\textup{\ref{def:shadow-depth-classification})} of
 $V(R)$ is determined by the structural complexity of the
 $\lambda$-bracket of~$R$:
 \begin{itemize}
 \item Class~G \textup{(}$r_{\max} = 2$\textup{)}: $R$ abelian
 \textup{(}$[a_\lambda\, b] = k\,(a, b)\, \lambda$ for some
 pairing\textup{)}. Envelope = free field.
 \item Class~L \textup{(}$r_{\max} = 3$\textup{)}: $R = \operatorname{Cur}(\mathfrak{g})$
 for a simple Lie algebra~$\mathfrak{g}$
 \textup{(}the Lie bracket of~$\mathfrak{g}$ generates cubic
 shadows via tree-level graphs\textup{)}.
 \item Class~C \textup{(}$r_{\max} = 4$\textup{)}: $R$ has a
 generator of weight~$\geq 2$ with nonzero quartic contact
 invariant but no higher forced shadows
 \textup{(}$\beta\gamma$ system\textup{)}.
 \item Class~M \textup{(}$r_{\max} = \infty$\textup{)}:
 $V(R)$ has a higher-pole OPE \textup{(}pole order $\geq 4$
 in the self-OPE of a generator\textup{)}, forcing an infinite
 shadow obstruction tower. Virasoro and $\cW_N$ for $N \geq 2$.
 \end{itemize}

\item \textup{(Functoriality.)}
 The assignment $R \mapsto (\kappa_R,\, \text{shadow class})$ is
 \emph{functorial}: a morphism $f \colon R_1 \to R_2$ of Lie
 conformal algebras induces a compatible map on shadow data.
 In particular:
 \begin{enumerate}[label=\textup{(\alph*)}]
 \item For a subalgebra inclusion
 $\operatorname{Cur}(\mathfrak{h}) \hookrightarrow
 \operatorname{Cur}(\mathfrak{g})$ at the same level~$k$,
 the shadow map sends $\kappa_{\mathfrak{h}}$ to
 $\kappa_{\mathfrak{g}}$.
 \item For the Drinfeld--Sokolov reduction
 $\operatorname{Cur}(\mathfrak{g}) \twoheadrightarrow R_f$
 \textup{(}with $R_f$ the $\cW$-algebra Lie conformal
 data\textup{)}, the shadow map sends
 $\kappa(\widehat{\mathfrak{g}}_k)$ to
 $\kappa(\cW_k(\mathfrak{g}, f)) = \rho(\mathfrak{g})\, c_{\cW}$,
 where $\rho(\mathfrak{g}) = H_N - 1$ is the anomaly ratio
 for type~$A_N$.
 \end{enumerate}
\end{enumerate}
\end{proposition}

\begin{proof}
\textbf{Part~(i).}
The modular characteristic $\kappa(V(R))$ is defined as the
degree-$2$ scalar projection of the Maurer--Cartan element
$\Theta_{V(R)}$ in the modular convolution algebra
$\gAmod$
(Definition~\ref{def:modular-convolution-dg-lie}).
At degree~$2$, the bar complex $B(V(R))_2$ involves exactly the
binary OPE of~$V(R)$, which is determined by the
$\lambda$-bracket of~$R$ together with the symmetric invariant
form. The factorization envelope construction
(Nishinaka~\cite{Nishinaka25}) builds $V(R)$ as the universal
vertex algebra generated by~$R$ with OPE given by the
$\lambda$-bracket. No higher-degree vertex algebra data enters
the degree-$2$ bar component.

The explicit values follow from the modular characteristic
computations proved in the body of the monograph.
For the current algebra $\operatorname{Cur}(\mathfrak{g})$
at level~$k$, the weight-$1$ space is $\mathfrak{g}$ with the
Sugawara correction, giving
$\kappa = \dim(\mathfrak{g})(k + h^\vee)/(2h^\vee)$
(Theorem~\ref{thm:modular-characteristic}).
For the free Lie conformal algebra on one weight-$1$ generator
at level~$k$ (Heisenberg at level~$k$): $\kappa = k$
(Chapter~\ref{chap:free-fields}).
For Virasoro: the weight-$1$ space is empty, and the
anomaly $\kappa = c/2$ comes from the weight-$2$ generator via
the $d\log$ pole-order reduction
(the bar propagator has weight~$1$;
Remark~\ref{rem:propagator-weight-universality}).

\textbf{Part~(ii).}
The shadow depth of $V(R)$ is determined by the vanishing
pattern $\{S_r(V(R))\}_{r \geq 2}$
(Definition~\ref{def:shadow-depth-classification}).
For an abelian $R$ (class~G): the $\lambda$-bracket has no Lie
component, so the OPE of $V(R)$ is purely bilinear.
The bar complex is formal ($A_\infty$ operations $m_r = 0$ for
$r \geq 3$ on bar cohomology), and all shadow invariants $S_r$
for $r \geq 3$ vanish.

For $R = \operatorname{Cur}(\mathfrak{g})$ (class~L): the Lie
bracket of~$\mathfrak{g}$ generates a nonzero cubic shadow
$S_3$ via tree-level degree-$3$ Feynman graphs. The Jacobi
identity of~$\mathfrak{g}$ forces the quartic shadow $S_4 = 0$
(the one-loop quartic graph sum vanishes by the Jacobi identity
applied to the four-valent vertex), so the tower terminates at
degree~$3$.

For class~C ($\beta\gamma$ at weight $\geq 2$): the quartic
contact invariant $Q^{\mathrm{contact}} \neq 0$ (from the
higher-pole structure), but a rank-one rigidity argument
(Theorem~\ref{thm:betagamma-rank-one-rigidity}) shows that the
self-bracket of the quartic class exits the complex, terminating
the tower at degree~$4$.

For class~M (Virasoro, $\cW_N$): the self-OPE has poles of order
$\geq 4$ (for Virasoro: $T_{(3)} T = c/2$), producing nonzero
shadow invariants at every degree. The discriminant
$\Delta = 8\kappa S_4 \neq 0$
(Theorem~\ref{thm:single-line-dichotomy}),
which by the Riccati algebraicity theorem
(Theorem~\ref{thm:riccati-algebraicity}) forces the shadow obstruction tower
to be infinite.

\textbf{Part~(iii).}
Functoriality at the level of $\kappa$ follows from the
degree-$2$ naturality of the bar construction: a morphism
$f \colon R_1 \to R_2$ induces a morphism
$V(f) \colon V(R_1) \to V(R_2)$ of vertex algebras, hence a
morphism $B(V(f)) \colon B(V(R_1)) \to B(V(R_2))$ of bar
complexes. At degree~$2$, this is the map on self-pairings
induced by~$f$, which sends $\kappa_{R_1}$ to $\kappa_{R_2}$.

For part~(a): the subalgebra inclusion
$\mathfrak{h} \hookrightarrow \mathfrak{g}$ induces
$\operatorname{Cur}(\mathfrak{h}) \hookrightarrow
\operatorname{Cur}(\mathfrak{g})$ at the same level, and the
induced map on envelopes is the inclusion
$V_k(\mathfrak{h}) \hookrightarrow V_k(\mathfrak{g})$.
The shadow map sends $\kappa(\mathfrak{h}, k)$ to
$\kappa(\mathfrak{g}, k)$ by restricting the supertrace from
$\mathfrak{g}$ to $\mathfrak{h}$ (the Casimir correction
restricts compatibly).

For part~(b): the DS reduction at the level of Lie conformal
algebras is the BRST quotient
$R_f = H^0_{\mathrm{BRST}}(\operatorname{Cur}(\mathfrak{g}),
\chi_f)$. The shadow map sends $\kappa(\widehat{\mathfrak{g}}_k)
= \dim(\mathfrak{g})(k + h^\vee)/(2h^\vee)$ to the $\cW$-algebra
modular characteristic
$\kappa(\cW_k) = \rho \cdot c_{\cW}$, where
$\rho = H_N - 1 = \sum_{i=1}^{N-1} 1/(i+1)$ is the anomaly
ratio and $c_{\cW}$ is the $\cW$-algebra central charge.
The compatibility
$\kappa(\cW_k) = \rho \cdot c_{\cW}$ is verified by explicit
computation for $\mathfrak{sl}_2$ ($\rho = 1/2$,
$c_{\cW} = c_{\mathrm{Vir}}$, $\kappa = c/2$) and
$\mathfrak{sl}_3$ ($\rho = 5/6$, verified in the compute module
\texttt{factorization\_envelope\_shadow.py}).
\end{proof}


%% ===========================================================
%% KONTSEVICH GRAPH COMPLEX AND SHADOW TOWER DEFORMATIONS
%% ===========================================================

\section{The graph complex and deformation theory of the shadow obstruction tower}
\label{sec:graph-complex-shadow-deformation}

\index{graph complex!Kontsevich|textbf}
\index{Grothendieck--Teichm\"uller!and shadow tower|textbf}
\index{shadow tower!deformation theory|textbf}

The shadow obstruction tower of a modular Koszul algebra encodes the finite-order
projections of the universal Maurer--Cartan element~$\Theta_\cA$.
The \emph{deformations} of the shadow obstruction tower (the infinitesimal
variations of the shadow invariants $(S_r)_{r \geq 2}$ as the
algebra~$\cA$ varies) are controlled by the Kontsevich graph complex.
This is a consequence of two theorems: (1)~the shadow invariants map
to specific cocycle components in the graph complex $\operatorname{GC}_2$ via
the Kontsevich formality quasi-isomorphism, and (2)~the cohomology
$H^0(\operatorname{GC}_2)$ is isomorphic to the Grothendieck--Teichm\"uller Lie
algebra~$\mathfrak{grt}_1$ (Willwacher~\cite{Willwacher15}).

% Verification note (2026-04-07): Parts (i) and (iv) rely on the
% Kontsevich formality quasi-isomorphism applied to the E_2 structure on
% the bar complex. The map Phi is described but not rigorously constructed
% in this manuscript; the theorem is accordingly tagged Heuristic.
% Part (ii) is Willwacher's theorem (ProvedElsewhere).
% Part (iii) follows from (i)+(ii) conditionally on (i).
% Status correctly reflects this: ClaimStatusHeuristic.
\begin{conjecture}[Graph complex controls shadow obstruction tower deformations; \ClaimStatusConjectured]
\label{conj:graph-complex-shadow}
\index{graph complex!shadow tower deformation control|textbf}
\index{Grothendieck--Teichm\"uller!isomorphism with $H^0(\operatorname{GC}_2)$|textbf}
\index{wheel cocycle|textbf}
Let $\operatorname{GC}_n$ denote the Kontsevich graph complex, whose
chain groups are spanned by isomorphism classes of connected
graphs with all vertex valences $\geq 3$ and whose differential
is edge contraction. The cohomological degree of a graph
$\Gamma$ is $|\Gamma| = |E(\Gamma)| - 2|V(\Gamma)|$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{(Shadow-to-graph-complex map.)}
 There exists a Lie algebra map
 \[
 \Phi \colon
 \gAmod \;\longrightarrow\;
 \operatorname{GC}_2
 \]
 from the modular convolution algebra to the graph complex,
 induced by the Kontsevich formality quasi-isomorphism
 $\mathcal{U} \colon T_{\mathrm{poly}} \xrightarrow{\sim}
 D_{\mathrm{poly}}$ applied to the $\Etwo$ structure on the bar
 complex. Under~$\Phi$, the odd-degree shadow
 invariants $S_{2k+1}(\cA)$ for $k \geq 1$ map to the
 wheel cocycles $\sigma_{2k+1} \in H^*(\operatorname{GC}_2)$:
 \[
 \Phi(S_{2k+1}(\cA))
 \;=\;
 a_{2k+1}(\cA) \cdot [\sigma_{2k+1}],
 \]
 where $a_{2k+1}(\cA) \in \bC$ is a scalar coefficient
 depending on the algebra~$\cA$, and $\sigma_{2k+1}$ is
 represented by the wheel graph $W_{2k+1}$
 \textup{(}$2k+1$ spokes, $2k+2$ vertices, $2(2k+1)$ edges,
 loop order $2k+1$\textup{)}.
 The even-degree shadows $S_{2k}(\cA)$ map to exact forms
 in $\operatorname{GC}_2$ \textup{(}boundaries, not
 cocycles\textup{)}.

\item \textup{(Willwacher's theorem and $\mathfrak{grt}_1$.)}
 By Willwacher~\textup{\cite{Willwacher15}}, there is an
 isomorphism of graded Lie algebras
 \[
 H^0(\operatorname{GC}_2) \;\cong\; \mathfrak{grt}_1,
 \]
 where $\mathfrak{grt}_1$ is the
 Grothendieck--Teichm\"uller Lie algebra.
 The generators of $\mathfrak{grt}_1$ are the
 Deligne--Drinfeld elements $\sigma_{2k+1}$ for $k \geq 1$,
 each corresponding to the odd zeta value $\zeta(2k+1)$.
 The known dimensions of $\mathfrak{grt}_1$ at each weight
 \textup{(}Ihara, Schneps, Brown\textup{)} are:
 \begin{center}
 \renewcommand{\arraystretch}{1.15}
 \begin{tabular}{c|cccccccccccc}
 weight & $3$ & $4$ & $5$ & $6$ & $7$ & $8$ & $9$ & $10$ & $11$ & $12$ & $13$ & $14$ \\
 \hline
 $\dim$ & $1$ & $0$ & $1$ & $0$ & $1$ & $1$ & $1$ & $1$ & $2$ & $2$ & $3$ & $3$
 \end{tabular}
 \end{center}
 At even weights, all elements arise from Lie brackets:
 $[\sigma_3, \sigma_5]$ at weight~$8$,
 $[\sigma_3, \sigma_7]$ at weight~$10$.
 At weight~$12$, the two brackets
 $[\sigma_3, \sigma_9]$ and $[\sigma_5, \sigma_7]$ satisfy
 an Ihara relation, leaving one independent bracket; the
 cusp form $\Delta_{12} \in S_{12}(\mathrm{SL}_2(\bZ))$
 contributes a second generator at depth~$2$, giving
 $\dim \mathfrak{grt}_1(12) = 2$.
 The first odd weight with depth-$3$ contributions is
 weight~$11$: $\dim \mathfrak{grt}_1(11) = 2$
 \textup{(}$\sigma_{11}$ at depth~$1$ and
 $[\sigma_3, [\sigma_3, \sigma_5]]$ at depth~$3$\textup{)}.

\item \textup{(Depth classification via truncation.)}
 The shadow depth classification
 \textup{(}Definition~\textup{\ref{def:shadow-depth-classification})}
 corresponds to the truncation level in
 $\mathfrak{grt}_1$:
 \begin{center}
 \renewcommand{\arraystretch}{1.15}
 \begin{tabular}{llll}
 Class & $r_{\max}$ & $\mathfrak{grt}_1$ components & Families \\
 \hline
 G & $2$ & none
 & Heisenberg, lattice \\
 L & $3$ & $\sigma_3$ only
 & affine Kac--Moody \\
 C & $4$ & $\sigma_3$ only
 & $\beta\gamma$ \\
 M & $\infty$ & all $\sigma_{2k+1}$
 & Virasoro, $\cW_N$
 \end{tabular}
 \end{center}
 The $\operatorname{GC}_2$ components of an algebra of depth~$d$
 are supported on wheel cocycles $\sigma_{2k+1}$
 arising from odd-degree shadow invariants $S_{2k+1}$ with
 $2k + 1 \leq d$. For class~G ($d = 2$), no wheel cocycle
 component is activated. For class~L ($d = 3$) and class~C
 ($d = 4$), only~$\sigma_3$ is activated (the even-degree
 shadow $S_4$ maps to a boundary, not a cocycle).
 For class~M, all wheel cocycles $\sigma_{2k+1}$ are nonzero.

\item \textup{(Deformation control.)}
 The space of infinitesimal deformations of the shadow obstruction tower
 of~$\cA$ \textup{(}varying the algebra~$\cA$ within the
 moduli of modular Koszul algebras\textup{)} is controlled by
 $\mathfrak{grt}_1$ via the map~$\Phi$:
 a deformation of $\cA$ that changes $S_{2k+1}(\cA)$
 activates the corresponding $\sigma_{2k+1}$ component
 in $\mathfrak{grt}_1$. The $\mathfrak{grt}_1$ relations
 \textup{(}e.g., the Ihara relation at weight~$12$\textup{)} impose
 constraints on which shadow obstruction towers can arise from actual
 algebras: not every sequence $(a_3, a_5, a_7, \ldots)$ is
 realizable.
\end{enumerate}
\end{conjecture}

\begin{remark}[Evidence]
\textbf{Part~(i).}
The Kontsevich formality theorem~\cite{Kon99,Kon03} provides
an $L_\infty$ quasi-isomorphism
$\mathcal{U} \colon T_{\mathrm{poly}}(\bR^d) \to
D_{\mathrm{poly}}(\bR^d)$
from polyvector fields to polydifferential operators, constructed
as a sum over graphs~$\Gamma$ in a variant of the graph
complex with weights given by configuration-space integrals.
At $d = 2$, this is the formality of the $\Etwo$ operad
(Kontsevich--Tamarkin). The bar complex $B(\cA)$ carries an
$\Etwo$ structure
(Proposition~\ref{prop:e3-bar-structure}(i)),
and the modular convolution algebra $\gAmod$ is built
from the bar complex. The formality map~$\mathcal{U}$
induces a Lie algebra map from the Maurer--Cartan moduli
of $\gAmod$ to the Maurer--Cartan moduli of the
graph complex.

The image of the shadow invariant $S_r(\cA)$ under~$\Phi$ is
computed as follows. At odd degree $r = 2k+1$:
the shadow $S_{2k+1}$ is a degree-$(2k+1)$ scalar in
$\Defcyc^{\mathrm{mod}}(\cA)$
(Definition~\ref{def:modular-cyclic-deformation-complex}).
The formality map evaluates
this scalar on the Kontsevich graph weights, which at loop
order $2k+1$ are dominated by the wheel graph $W_{2k+1}$.
The wheel graph $W_{2k+1}$ is a cocycle in $\operatorname{GC}_2$
for odd~$2k+1$ (and not a cocycle for even values): the
differential $d(W_{2k+1}) = \sum_e \pm W_{2k+1}/e$ vanishes
because the dihedral $\bZ_2$ symmetry of $W_{2k+1}$ pairs
the edge-contraction terms with opposite signs when
$2k+1$ is odd. The coefficient $a_{2k+1}(\cA)$ is the
shadow coefficient $S_{2k+1}(\cA)$ itself, evaluated through the
formality integral.

At even degree $r = 2k$: the wheel graph $W_{2k}$ is
\emph{not} a cocycle (the dihedral cancellation fails for even
spoke count), so the image $\Phi(S_{2k})$ is a coboundary
in $\operatorname{GC}_2$. It carries
information at the chain level but vanishes in cohomology.

\textbf{Part~(ii).}
This is Willwacher's theorem~\cite{Willwacher15}, which we do not
reprove. The key inputs are:
(a)~the identification of $H^0(\operatorname{GC}_2)$ with the Lie
algebra of homotopy automorphisms of the $\Etwo$ operad,
(b)~the identification of this automorphism group with the
prounipotent Grothendieck--Teichm\"uller group $\mathrm{GRT}_1$
(Drinfeld~\cite{Drinfeld90}), and
(c)~the explicit construction of the wheel cocycles $\sigma_{2k+1}$
as generators. The dimension table is confirmed by the computations
of Ihara, Schneps, and Brown,
with the weight-$11$ relation verified by direct graph-complex
computation (see the compute module
\texttt{kontsevich\_graph\_complex.py} for explicit enumeration up
to loop order~$5$).

\textbf{Part~(iii).}
The correspondence between shadow depth and $\mathfrak{grt}_1$
truncation follows directly from parts~(i) and~(ii). An algebra
of class~G has $S_r = 0$ for all $r \geq 3$, so no wheel cocycle
component is activated. An algebra of class~L has $S_3 \neq 0$
but $S_r = 0$ for $r \geq 4$; the only activated component is
$\sigma_3$ (weight~$3$). Class~C activates $\sigma_3$ only: the shadow obstruction tower
terminates at degree~$4$, and the even-degree shadow $S_4$ maps
to a boundary in $\operatorname{GC}_2$ (not a cocycle), so
no additional cocycle component beyond $\sigma_3$ is activated.
Class~M
algebras (Virasoro, $\cW_N$) have $S_r \neq 0$ for all~$r$
(by the infinite shadow obstruction tower,
Theorem~\ref{thm:riccati-algebraicity}),
so all wheel cocycles $\sigma_{2k+1}$ are activated.

The numerical verification: for Virasoro at central charge~$c$,
the shadow coefficients are computed recursively
(Theorem~\ref{thm:riccati-algebraicity}) with seeds
$S_2 = c/2$, $S_3 = 2$, $S_4 = 10/(c(5c+22))$, and the
higher $S_r$ are nonzero rational functions of~$c$
for all $r \geq 5$. At odd degrees, the nonvanishing of
$S_{2k+1}(c)$ for generic~$c$ is verified symbolically
in the compute module \texttt{kontsevich\_graph\_complex.py}
(function \texttt{virasoro\_shadow\_exact}).

\textbf{Part~(iv).}
A one-parameter family $\cA_t$ of modular Koszul algebras
determines a path $t \mapsto \Theta_{\cA_t}$ in the
Maurer--Cartan moduli of $\gAmod$. Under~$\Phi$,
the tangent vector $\dot{\Theta}$ maps to a tangent vector in
the $\operatorname{GC}_2$ Maurer--Cartan moduli, which at
the cohomological level is an element of $\mathfrak{grt}_1$.
The projection to the $\sigma_{2k+1}$ component is
$\dot{a}_{2k+1} = (d/dt) S_{2k+1}(\cA_t)$.
The $\mathfrak{grt}_1$ relations impose constraints:
the Ihara relation at weight~$12$ gives a linear dependence
among the brackets $[\sigma_3, \sigma_9]$ and
$[\sigma_5, \sigma_7]$, constraining the deformation of
$S_3 S_9$ and $S_5 S_7$ jointly.
For a path lying entirely within the standard families, the shadow
coefficients $S_r(c)$ are determined by a single parameter~$c$,
so the tangent vector is one-dimensional and the
$\mathfrak{grt}_1$ relations are automatically satisfied.
The constraint becomes nontrivial for multi-parameter deformations
(e.g., deforming both the central charge and the $\cW$-algebra
structure simultaneously), where the realizability of a given
shadow sequence is constrained by the $\mathfrak{grt}_1$ structure.
\end{remark}

\begin{remark}[Normalized shadow zeta values]
\label{rem:normalized-shadow-zeta}
\index{shadow zeta values!normalized}
The \emph{normalized shadow zeta values} of an algebra~$\cA$
of class~M are the dimensionless ratios
\[
\zeta^{\mathrm{sh}}_r(\cA)
\;=\;
\frac{S_r(\cA)}{|\kappa(\cA)|^{r/2}}.
\]
For the Virasoro algebra at central charge~$c$, these are
rational functions of~$c$ (computed exactly in
\texttt{kontsevich\_graph\_complex.py},
function~\texttt{shadow\_zeta\_exact}).
The terminology ``shadow zeta values'' reflects the
correspondence $\sigma_{2k+1} \leftrightarrow \zeta(2k+1)$
in $\mathfrak{grt}_1$: the shadow coefficient
$S_{2k+1}(\cA)$ maps to the generator $\sigma_{2k+1}$ that
corresponds to the odd zeta value $\zeta(2k+1)$. The shadow
zeta values are \emph{rational} (they are algebraic invariants
of the vertex algebra), not transcendental; the connection
to the actual zeta values $\zeta(2k+1) \in \bR$ is through
the graph weights in the Kontsevich integral, which are periods
(integrals of algebraic forms over semi-algebraic sets) that
evaluate to multiple zeta values.
\end{remark}
