\chapter{Chiral Hochschild cohomology and Koszul duality}
\label{chap:deformation-theory}
\index{deformation theory!chiral|textbf}
\index{Hochschild cohomology!chiral|textbf}

The fiberwise curvature $\dfib^{\,2} = \kappa \cdot \omega_1$ at genus~$1$ (Chapter~\ref{ch:heisenberg-frame}; Convention~\ref{conv:higher-genus-differentials}) makes the bar complex a curved $A_\infty$-algebra rather than a chain complex.  This chapter develops the deformation-obstruction theory organizing these quantum corrections.

\begin{remark}[Semantic levels; Convention~\ref{conv:hms-levels}]
\label{rem:deformation-theory-hms}
Deformation complexes and curved $A_\infty$ structures are constructed at \textbf{M-level}.  Obstruction scalars ($\kappa$), periodicity numbers, and the complementarity pairing are \textbf{S-level} shadows.  The full modular characteristic $\Theta_{\cA}$ (Conjecture~\ref{conj:universal-theta}) is a conjectured \textbf{H-level} structure; its scalar shadow $\kappa(\cA)$ is proved.
\end{remark}

\section{The deformation problem for chiral algebras}

Classically, $HH^2$ parametrizes deformations and $HH^3$ carries obstructions.  For chiral algebras, $\overline{\mathcal{M}}_g$ contributes its own cohomology, splitting the theory into genus-$0$ (algebraic) and higher-genus (modular) components.
The complementarity theorem
(Theorem~\ref{thm:quantum-complementarity-main}) gives the answer:
$Q_g(\cA)$ and $Q_g(\cA^!)$ are complementary Lagrangians
in a shifted-symplectic ambient space.  Koszul duality sends $HH^n(\cA)$ to $HH^{2-n}(\cA^!)^\vee \otimes \omega_X$
(Remark~\ref{rem:nc-hodge-degeneration}).

\subsection{Origins and physical motivation}

Exactly marginal CFT deformations correspond to closed Hochschild $2$-cocycles (Seiberg~\cite{Sei88}); the algebraic framework is Gerstenhaber's deformation theory~\cite{Ger63}, extended to chiral algebras via Beilinson--Drinfeld's factorization formalism~\cite{BD04}.  Classically, $HH^2(A,A)$ parametrizes infinitesimal deformations and $HH^3(A,A)$ carries obstructions (Chapter~\ref{ch:algebraic-foundations}).
\index{obstruction theory|textbf}
A chiral deformation must preserve the $\mathcal{D}_X$-module structure, the chiral multiplication, the diagonal singularity structure, and the OPE coefficients.

\subsection{Configuration spaces in deformation theory}

Configuration spaces appear because the nontrivial algebraic structure of a chiral algebra is concentrated along collision loci. On a curve $X$, the commutator $[\phi_1(z_1), \phi_2(z_2)]$ vanishes for $z_1 \neq z_2$; all structure is encoded in the approach $z_1 \to z_2$.

The configuration space $C_n(X) = \{(z_1,\ldots,z_n) \in X^n : z_i \neq z_j\}$ parametrizes positions where operators do not collide. Its compactification $\overline{C}_n(X)$ adds boundary divisors $D_{ij} = \{z_i = z_j\}$ that encode collision limits. A deformation of the chiral algebra must specify how the algebraic structure changes as points approach these divisors.

\section{Construction of the chiral Hochschild complex}

\subsection{The cochain spaces}

\begin{definition}[Chiral Hochschild complex, geometric realization]
For a chiral algebra $\mathcal{A}$ on a smooth curve $X$, define the degree $n$ cochains as
\[
C^n_{\text{chiral}}(\mathcal{A}) = \Gamma\left(\overline{C}_{n+2}(X), j_*j^*\mathcal{A}^{\boxtimes (n+2)} \otimes \Omega^n_{\overline{C}_{n+2}(X)}(\log D)\right)
\]
where:
\begin{itemize}
\item $\overline{C}_{n+2}(X)$ is the Fulton--MacPherson compactification
\item $j: C_{n+2}(X) \to \overline{C}_{n+2}(X)$ is the open embedding
\item $\mathcal{A}^{\boxtimes (n+2)}$ denotes the external tensor product on $X^{n+2}$
\item $\Omega^n_{\overline{C}_{n+2}(X)}(\log D)$ are $n$-forms with logarithmic poles along the boundary divisor $D$
\end{itemize}
\end{definition}

The index $n+2$ (rather than $n$) appears because Hochschild cohomology involves one output, $n$ inputs, and one evaluation point. Explicitly, a degree $n$ cochain is a sum of expressions
\[
\phi = \sum_I a_0^{(I)}(z_0) \otimes a_1^{(I)}(z_1) \otimes \cdots \otimes a_n^{(I)}(z_n) \otimes a_{\infty}^{(I)}(z_{\infty}) \otimes \omega_I
\]
where $a_i^{(I)} \in \mathcal{A}$ and $\omega_I$ is an $n$-form on $\overline{C}_{n+2}(X)$ with logarithmic singularities.

\subsection{The differential: three components united}

The differential $d: C^n_{\text{chiral}} \to C^{n+1}_{\text{chiral}}$ has three components reflecting the algebraic, geometric, and operadic structures:

\begin{theorem}[The chiral Hochschild differential; \ClaimStatusProvedHere]
\label{thm:chiral-hochschild-differential}
The differential decomposes as
\[
d = d_{\text{int}} + d_{\text{fact}} + d_{\text{config}}
\]
where:
\begin{enumerate}
\item $d_{\text{int}}$: internal differential from the $\mathcal{D}_X$-module structure
\item $d_{\text{fact}}$: factorization using chiral multiplication  
\item $d_{\text{config}}$: de Rham differential on configuration space
\end{enumerate}
\end{theorem}

\begin{proof}
We expand $d^2 = (d_{\text{int}} + d_{\text{fact}}
+ d_{\text{config}})^2$ into six terms (three squares and
three anticommutators) and verify that each vanishes on a
generic cochain $\phi \in C^n_{\text{chiral}}$.

\emph{(I) Pure squares.}

\emph{(I.1)} $d_{\text{int}}^2(\phi) = 0$.
The internal differential $d_{\text{int}}$ acts on each
tensor factor $a_i$ by the $\mathcal{D}_X$-module differential
$d_\mathcal{A}$, alternating signs.  Since $d_\mathcal{A}^2 = 0$
and the signs follow the standard Koszul rule, this is the
usual chain complex identity.

\emph{(I.2)} $d_{\text{config}}^2(\phi) = 0$.
$d_{\text{config}} = d_{\overline{C}_{n+2}(X)}$ is the
de~Rham differential on the compactified configuration space.
Since $d_{\mathrm{dR}}^2 = 0$, this is immediate.

\emph{(I.3)} $d_{\text{fact}}^2(\phi) = 0$.
Applied to $\phi \in C^n$, $d_{\text{fact}}^2$ composes two
chiral multiplications at distinct pairs of colliding points.
For each pair of collisions $(z_i = z_j)$ and $(z_k = z_l)$
with $\{i,j\} \cap \{k,l\} = \varnothing$, the two residue
extractions commute.  For overlapping pairs (sharing a point),
the double residue
$\mathrm{Res}_{z_i = z_j}\mathrm{Res}_{z_j = z_k}$ is the
iterated OPE, which cancels with
$\mathrm{Res}_{z_j = z_k}\mathrm{Res}_{z_i = z_j}$ by
associativity of the chiral product: $\mu \circ (\mu \otimes
\mathrm{id}) = \mu \circ (\mathrm{id} \otimes \mu)$ on the
localizations $j_*j^*$ (the Borcherds identity).

\emph{(II) Mixed anticommutators.}

\emph{(II.1)} $\{d_{\text{int}}, d_{\text{fact}}\}(\phi) = 0$.
The chiral product $\mu\colon j_*j^*(\mathcal{A} \boxtimes
\mathcal{A}) \to \Delta_*\mathcal{A}$ is a morphism of
$\mathcal{D}_X$-modules, so $d_\mathcal{A} \circ \mu =
\mu \circ (d_\mathcal{A} \boxtimes \mathrm{id} +
\mathrm{id} \boxtimes d_\mathcal{A})$.  Expanding the
anticommutator term by term, each
$d_\mathcal{A}(\mu(a_i, a_j))$ equals
$\mu(d_\mathcal{A} a_i, a_j) + (-1)^{|a_i|}
\mu(a_i, d_\mathcal{A} a_j)$,
and the signs from $d_{\text{int}}$ and $d_{\text{fact}}$
cancel pairwise.

\emph{(II.2)} $\{d_{\text{int}}, d_{\text{config}}\}(\phi) = 0$.
The logarithmic forms
$\omega \in \Omega^*_{\overline{C}_{n+2}}(\log D)$
are \emph{universal}: they depend only on the configuration
space coordinates $z_i$, not on the algebra data $a_i$.
Therefore $d_\mathcal{A}$ acts only on the $a_i$ factors,
while $d_{\mathrm{dR}}$ acts only on $\omega$.  Since the
two differentials act on different tensor factors:
$d_\mathcal{A}(a_i \otimes \omega) =
(d_\mathcal{A} a_i) \otimes \omega$ and
$d_{\mathrm{dR}}(a_i \otimes \omega) =
a_i \otimes d_{\mathrm{dR}}\omega$,
the anticommutator reduces to
$(d_\mathcal{A} \otimes d_{\mathrm{dR}} +
d_{\mathrm{dR}} \otimes d_\mathcal{A})(a_i \otimes \omega)
= 0$ by the Koszul sign rule for the tensor product of
chain complexes.

\emph{(II.3)} $\{d_{\text{fact}}, d_{\text{config}}\}(\phi) = 0$.
This is the essential cancellation, requiring the
Arnold--Orlik--Solomon relations.

On a degree-$1$ cochain
$\phi = a_1 \otimes a_2 \otimes a_3 \otimes
\eta_{12} \in C^1$ (the smallest nontrivial case,
with three points $z_1, z_2, z_3$), the two compositions act
as:
\begin{align*}
(d_{\text{config}} \circ d_{\text{fact}})(\phi)
&= d_{\mathrm{dR}}\Bigl(
  \mathrm{Res}_{z_1 = z_2}\bigl[a_1 a_2 \otimes a_3
    \otimes \eta_{12}\bigr] \Bigr), \\
(d_{\text{fact}} \circ d_{\text{config}})(\phi)
&= \sum_{i<j}
  \mathrm{Res}_{z_i = z_j}\bigl[a_1 \otimes a_2 \otimes a_3
    \otimes d_{\mathrm{dR}}\eta_{12}\bigr].
\end{align*}
The key identity is Arnold's relation
\cite{Arn69}: for the logarithmic 1-forms
$\eta_{ij} = d\log(z_i - z_j)$ on $C_3(X)$,
\begin{equation}\label{eq:arnold-three-point}
\eta_{12} \wedge \eta_{23}
+ \eta_{23} \wedge \eta_{31}
+ \eta_{31} \wedge \eta_{12} = 0.
\end{equation}
Equivalently, $d_{\mathrm{dR}}\eta_{12}$ (which is
supported on the boundary divisor) decomposes as a sum of
residues at $D_{13}$ and $D_{23}$:
\[
d_{\mathrm{dR}}(\eta_{12})
\;\equiv\;
-\eta_{23}\big|_{D_{12}} - \eta_{31}\big|_{D_{12}}
\pmod{\text{smooth forms}}.
\]
In each residue term, $d_{\text{fact}}$ extracts the OPE
at a collision, and $d_{\text{config}}$ produces the
boundary form.  The Arnold relation
\eqref{eq:arnold-three-point} ensures these contributions
cancel pairwise, yielding
$\{d_{\text{fact}}, d_{\text{config}}\}(\phi) = 0$.

For general $n$, the argument extends by applying the
generalized Arnold relations on $\overline{C}_{n+2}(X)$
(Theorem~\ref{thm:arnold-relations}): every boundary
stratum of $\overline{C}_{n+2}$ where two points collide
contributes a residue (from $d_{\text{fact}}$) and a
boundary form (from $d_{\text{config}}$), and the
Arnold relations ensure these pair up with opposite signs.
\end{proof}

\subsection{Explicit formula for the differential}

For a cochain $\phi \in C^n_{\text{chiral}}$, the differential acts by:

\begin{align}
(d_{\text{int}}\phi)(&z_0,\ldots,z_{n+1}) = \sum_{i=0}^{n+1} (-1)^i d_{\mathcal{A}}(\phi(z_0,\ldots,\hat{z}_i,\ldots,z_{n+1})) \\
(d_{\text{fact}}\phi)(&z_0,\ldots,z_{n+1}) = \sum_{i=1}^n (-1)^i \text{Res}_{z_i = z_0} \phi(\mu(z_0,z_i),z_1,\ldots,\hat{z}_i,\ldots,z_{n+1}) \\
&+ \sum_{1 \leq i < j \leq n} (-1)^{i+j} \phi(z_0,\ldots,\mu(z_i,z_j),\ldots,\hat{z}_i,\ldots,\hat{z}_j,\ldots,z_{n+1}) \\
(d_{\text{config}}\phi)(&z_0,\ldots,z_{n+1}) = d_{\overline{C}_{n+2}}(\phi)
\end{align}

where $\hat{z}_i$ denotes omission and $\mu$ is the chiral multiplication.

\section{Computing cohomology via bar-cobar resolution}

\subsection{The resolution strategy}

\begin{theorem}[Hochschild via bar-cobar; \ClaimStatusProvedHere]
\textup{[Regime: quadratic on the Koszul locus
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

For any chiral Koszul algebra $\mathcal{A}$
\textup{(}Definition~\textup{\ref{def:chiral-koszul-pair})},
there is a quasi-isomorphism
\[
C^{\bullet}_{\text{chiral}}(\mathcal{A}) \simeq \text{Hom}_{\text{ChirAlg}}(\Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A})), \mathcal{A})
\]
where $\Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A}))$ is the cobar construction of the bar complex.
\end{theorem}

\begin{proof}
The proof has three steps:

\emph{Step 1: Bar gives cofree resolution.} 
The geometric bar complex $\overline{B}^{\text{ch}}(\mathcal{A})$ constructed in Chapter~\ref{chap:bar-cobar} is a cofree chiral coalgebra resolving $\mathcal{A}$:
\[
\overline{B}^{\text{ch}}(\mathcal{A}) \xrightarrow{\epsilon} \mathcal{A}
\]

\emph{Step 2: Cobar gives free resolution.}
Applying the cobar functor (Chapter~\ref{chap:bar-cobar}) yields a free chiral algebra resolution:
\[
\Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A})) \xrightarrow{\eta} \mathcal{A}
\]

\emph{Step 3: Hom computes Ext.}
By definition, 
\[
\text{Ext}^n_{\text{ChirAlg}}(\mathcal{A}, \mathcal{A}) = H^n(\text{Hom}_{\text{ChirAlg}}(\Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A})), \mathcal{A}))
\]
The left side is precisely $HH^n_{\text{chiral}}(\mathcal{A})$ by definition.
\end{proof}

\subsection{The spectral sequence}

\begin{theorem}[Hochschild spectral sequence; \ClaimStatusProvedHere]
There exists a spectral sequence
\[
E_1^{n,q} = H^q(\overline{C}_{n+2}(X), \mathcal{A}^{\boxtimes (n+2)} \otimes \Omega^n_{\log}) \Rightarrow HH^{n+q}_{\text{chiral}}(\mathcal{A})
\]
where $n$ is the bar degree (number of internal insertions) and $q$ is the sheaf cohomology degree, which are independent indices.
\end{theorem}

\begin{proof}
The chiral Hochschild complex $CH^*(\mathcal{A})$ is a double complex with horizontal differential $d_{\mathrm{bar}}$ (the bar differential of Theorem~\ref{thm:bar-differential}) and vertical differential $d_{\mathrm{sheaf}}$ (sheaf cohomology on configuration spaces).  Filter by bar degree: $F^n = \bigoplus_{m \geq n} CH^{m,*}$.  The resulting spectral sequence has $E_0^{n,q} = \Gamma(\overline{C}_{n+2}(X), \mathcal{A}^{\boxtimes(n+2)} \otimes \Omega^n_{\log})$ with $d_0 = d_{\mathrm{sheaf}}$, so $E_1^{n,q} = H^q(\overline{C}_{n+2}(X), \mathcal{A}^{\boxtimes(n+2)} \otimes \Omega^n_{\log})$.  Convergence follows from the bounded-below hypothesis on $\mathcal{A}$ and the finite cohomological dimension of configuration spaces.
\end{proof}

For the cyclic refinement relating Hochschild to cyclic homology via Connes' operator, see Theorem~\ref{thm:HC-spectral-sequence}.  For formal chiral algebras (quasi-isomorphic to their cohomology), the spectral sequence above degenerates at $E_1$, giving:
\[
HH^k_{\text{chiral}}(\mathcal{A}) \cong \bigoplus_{n+q=k} H^q(\overline{C}_{n+2}(X), \mathcal{A}^{\boxtimes (n+2)} \otimes \Omega^n_{\log})
\]

\section{Koszul duality for chiral algebras}

\subsection{Quadratic chiral algebras and their duals}

\begin{definition}[Quadratic chiral algebra]
A chiral algebra $\mathcal{A}$ is \emph{quadratic} if it admits a presentation
\[
\mathcal{A} = T_{\text{chiral}}(\mathcal{V})/(R)
\]
where:
\begin{itemize}
\item $\mathcal{V}$ is a locally free $\mathcal{O}_X$-module of generators
\item $T_{\text{chiral}}(\mathcal{V})$ is the free chiral algebra on $\mathcal{V}$
\item $R \subset j_*j^*(\mathcal{V} \boxtimes \mathcal{V})$ consists of quadratic relations
\end{itemize}
\end{definition}

The free chiral algebra requires care to define. Following Beilinson--Drinfeld:

\begin{definition}[Free chiral algebra]
The free chiral algebra on $\mathcal{V}$ is
\[
T_{\text{chiral}}(\mathcal{V}) = \bigoplus_{n \geq 0} \pi_{n*}\left(j_*j^*\mathcal{V}^{\boxtimes n} \otimes \mathcal{D}_{C_n(X)/X}\right)^{\Sigma_n}
\]
where $\pi_n: C_n(X) \to X$ is the projection and $\mathcal{D}_{C_n(X)/X}$ denotes relative differential operators.
\end{definition}

\begin{definition}[Koszul dual]
The Koszul dual of a quadratic chiral algebra $\mathcal{A}$ is
\[
\mathcal{A}^! = T_{\text{chiral}}(\mathcal{V}^*)/(R^{\perp})
\]
where:
\begin{itemize}
\item $\mathcal{V}^* = \mathcal{H}om_{\mathcal{O}_X}(\mathcal{V}, \omega_X)$ is the dual shifted by the canonical bundle
\item $R^{\perp}$ consists of relations orthogonal to $R$ under the canonical pairing
\[
\langle \cdot, \cdot \rangle: j_*j^*(\mathcal{V}^* \boxtimes \mathcal{V}) \to j_*\omega_{X^2 \setminus \Delta}
\]
\end{itemize}
\end{definition}

\begin{remark}[Interpretation]\label{rem:koszul-dual-meaning}
The Koszul dual $\mathcal{A}^!$ is the coalgebra that the bar construction produces from $\mathcal{A}$. More precisely:

\begin{enumerate}
\item \emph{Generator duality}: The generators of $\mathcal{A}^!$ are the duals of the generators of $\mathcal{A}$:
   $$\mathcal{V}^* = \mathcal{H}om_{\mathcal{O}_X}(\mathcal{V}, \omega_X)$$
   This means: if $\mathcal{A}$ has generators $\phi_1, \ldots, \phi_n$, then $\mathcal{A}^!$ has dual generators $\phi_1^*, \ldots, \phi_n^*$

\item \emph{Relation orthogonality}: The relations $R^{\perp}$ in $\mathcal{A}^!$ are orthogonal to the relations $R$ in $\mathcal{A}$ under the residue pairing:
   $$\langle r, r^* \rangle = \int_{X^2 \setminus \Delta} r \wedge r^* = 0 \quad \text{for all } r \in R, r^* \in R^{\perp}$$
   This means: what is a relation in $\mathcal{A}$ becomes ``freedom'' in $\mathcal{A}^!$, and vice versa

\item \emph{Bar computes this dual}: The bar construction $\bar{B}^{\text{ch}}(\mathcal{A})$ naturally produces a coalgebra whose generators are $\mathcal{V}^*$ and whose coproduct encodes the relations $R^{\perp}$
\end{enumerate}

Therefore, saying $\bar{B}^{\text{ch}}(\mathcal{A}) \simeq \mathcal{A}^!$ is not a new condition but rather a \emph{verification} that the bar construction does what we expect: it produces the Koszul dual coalgebra.
\end{remark}

\begin{example}[Explicit correspondence for Heisenberg]
For the Heisenberg chiral algebra $\mathcal{H}$ with generator $\alpha(z)$ and OPE:
$$\alpha(z)\alpha(w) \sim \frac{1}{(z-w)^2}$$

The Koszul dual $\mathcal{H}^!$ has:
\begin{itemize}
\item \emph{Dual generator}: $\alpha^*(z)$ with $\langle \alpha, \alpha^* \rangle = 1$ under residue pairing
\item \emph{Coproduct}: 
   $$\Delta(\alpha^*) = \alpha^* \otimes 1 + 1 \otimes \alpha^* + \text{(higher order terms)}$$
   encoding the dual of the commutative algebra structure
\item \emph{Bar construction}: $\bar{B}^{\text{ch}}(\mathcal{H})$ consists of forms like:
   $$\alpha(z_1) \otimes \cdots \otimes \alpha(z_n) \otimes \eta_{12} \wedge \eta_{23} \wedge \cdots$$
   whose residues extract the coproduct coefficients
\end{itemize}

The cobar $\Omega^{\text{ch}}(\mathcal{H}^!)$ reconstructs a commutative chiral algebra from this coalgebraic data.
\end{example}

\begin{remark}[Koszul dual versus dual]
The term ``Koszul dual'' (rather than just ``dual'') emphasizes that:
\begin{enumerate}
\item This is a derived/homotopical notion (quasi-isomorphisms, not isomorphisms)
\item It involves a specific homological construction (bar-cobar)
\item It generalizes the classical Koszul duality for quadratic algebras
\item The duality is self-inverse: $(\mathcal{A}^!)^! \simeq \mathcal{A}$
\end{enumerate}

When $\mathcal{A}$ is quadratic, $\mathcal{A}^!$ recovers the classical quadratic dual. For non-quadratic chiral algebras, $\mathcal{A}^!$ is defined by the bar construction but maintains all the essential dualities.
\end{remark}

\subsection{The universal twisting morphism}

\begin{definition}[Universal twisting morphism]
A \emph{twisting morphism} $\tau: \mathcal{A}^! \to \mathcal{A}$ is a degree 1 map satisfying the Maurer--Cartan equation
\[
\partial \tau + \tau \star \tau = 0
\]
where $\star$ denotes convolution in $\text{Hom}(\overline{B}^{\text{ch}}(\mathcal{A}^!), \Omega^{\text{ch}}(\overline{B}^{\text{ch}}(\mathcal{A})))$.
\end{definition}

\begin{theorem}[Existence and uniqueness {\cite{LV}}; \ClaimStatusProvedElsewhere]
For a Koszul pair $(\mathcal{A}, \mathcal{A}^!)$, there exists a unique universal twisting morphism $\tau: \mathcal{A}^! \to \mathcal{A}$ that induces quasi-isomorphisms:
\begin{align}
\mathcal{A}^!_{\tau} &\simeq \overline{B}^{\text{ch}}(\mathcal{A}) \\
\mathcal{A}_{\tau} &\simeq \Omega^{\text{ch}}(\mathcal{A}^!)
\end{align}
where the subscript denotes twisting by $\tau$.
\end{theorem}

\begin{remark}[What the twisting morphism does]\label{rem:twisting-morphism-meaning}
The twisting morphism $\tau$ is the \emph{explicit map implementing the bar-cobar isomorphism}. Concretely:

\begin{enumerate}
\item \emph{Direction}: $\tau: \mathcal{A}^! \to \mathcal{A}$ is a map from the dual coalgebra to the original algebra

\item \emph{Maurer--Cartan equation}: The condition $\partial \tau + \tau \star \tau = 0$ ensures that $\tau$ intertwines the coalgebra differential on $\mathcal{A}^!$ with the algebra differential on $\mathcal{A}$

\item \emph{Twisted structures}: 
   \begin{itemize}
   \item $\mathcal{A}^!_{\tau}$ is $\mathcal{A}^!$ with differential twisted by $\tau$
   \item $\mathcal{A}_{\tau}$ is $\mathcal{A}$ with structure twisted by $\tau$
   \item The theorem says these twisted structures are quasi-isomorphic to bar and cobar
   \end{itemize}

\item \emph{Universality}: $\tau$ is universal in that any other twisting factors through it
\end{enumerate}

Geometrically, $\tau$ is realized by:
$$\tau(c) = \int_{C_2(X)} \text{ev}^* c \wedge K_{\text{twist}}$$
where $K_{\text{twist}}$ is a universal integration kernel on the configuration space.
\end{remark}

\begin{example}[Twisting for fermion-boson duality]
For the Koszul pair (free fermions $\mathcal{F}$, $\beta\gamma$ system $\mathcal{BG}$):

The twisting morphism $\tau: \mathcal{F}^! \to \mathcal{F}$ is given by:
$$\tau(\psi^*)(z) = \int_{\mathbb{C}} \psi(w) \cdot \frac{dw}{(z-w)}$$

This map:
\begin{itemize}
\item Takes the dual generator $\psi^*$ of $\mathcal{F}^!$
\item Integrates it against the fermion field $\psi$ with the basic kernel $\frac{1}{z-w}$
\item Produces a twisted field that satisfies bosonic commutation relations
\item Implements the fermion-boson correspondence at the level of Maurer--Cartan elements
\end{itemize}

The Maurer--Cartan equation $\partial \tau + \tau \star \tau = 0$ becomes the statement that this construction is consistent with the OPE structures on both sides.
\end{example}

\subsection{Main duality theorem}\label{subsec:hochschild-duality}

\begin{theorem}[Koszul duality for Hochschild cohomology
\textup{(}Theorem~H\textup{)}; \ClaimStatusProvedHere]
\label{thm:main-koszul-hoch}
\index{Hochschild cohomology!Koszul duality|textbf}
\textup{[Regime: quadratic on the Koszul locus
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

For every chiral Koszul datum~$\cA$
\textup{(}Definition~\textup{\ref{def:chiral-koszul-morphism})} with
dual~$\cA^!$ on a smooth projective curve~$X$, the bigraded chiral
Hochschild complex
\textup{(}Definition~\textup{\ref{def:bigraded-hochschild})} satisfies
the \emph{derived-level} duality:
\begin{equation}\label{eq:hochschild-H-derived}
RHH_{\mathrm{ch}}(\cA)
\;\simeq\;
R\mathrm{Hom}\bigl(RHH_{\mathrm{ch}}(\cA^!),\, \omega_X[2]\bigr).
\end{equation}
On cohomology:
\[
HH^n_{\mathrm{chiral}}(\mathcal{A}) \cong HH^{2-n}_{\mathrm{chiral}}(\mathcal{A}^!)^{\vee} \otimes \omega_X.
\]
The shift by~$2$ is the collapsed trace of the variable Verdier
shift~$p+2$ at bar degree~$p$: Koszul concentration
\textup{(}Theorem~\textup{\ref{thm:bar-concentration})} forces
$p = q$ on the surviving diagonal, so the variable
shift collapses to the constant~$2$
\textup{(}Remark~\textup{\ref{rem:hochschild-shift-origin})}.
The $\omega_X$ twist encodes the dualizing sheaf.
\end{theorem}

\begin{proof}
We give two arguments; the first is more explicit, the second more conceptual.

\medskip\noindent\emph{First proof: via bar-cobar duality.}
The bar-cobar quasi-isomorphism (Theorem~\ref{thm:bar-cobar-isomorphism-main}),
extended to all genera by Theorem~\ref{thm:higher-genus-inversion}, gives an
equivalence of $\mathcal{D}$-module complexes on $\overline{C}_{n+2}(X)$:
\[
\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A}))
\xrightarrow{\;\sim\;} \mathcal{A}.
\]
Since $(\mathcal{A}, \mathcal{A}^!)$ is a Koszul pair, the bar construction
computes the Koszul dual:
$\bar{B}^{\mathrm{ch}}(\mathcal{A}) \simeq \mathcal{A}^!$
(Theorem~\ref{thm:e1-chiral-koszul-duality}).  Therefore:
\begin{align}
HH^n_{\mathrm{chiral}}(\mathcal{A})
&= \mathrm{Ext}^n_{\mathrm{ChirAlg}}(\mathcal{A}, \mathcal{A}) \notag \\
&\cong H^n\bigl(\mathrm{Hom}(\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A})), \mathcal{A})\bigr) \notag \\
&\cong H^n\bigl(\mathrm{Hom}(\Omega^{\mathrm{ch}}(\mathcal{A}^!), \mathcal{A})\bigr). \label{eq:hh-via-hom}
\end{align}

The chiral Hochschild complex in bar degree~$n$ lives on
$\overline{C}_{n+2}(X)$, a smooth proper variety of complex dimension~$n+2$
(since $\dim_{\mathbb{C}} X = 1$ and FM compactification preserves smoothness).
Serre--Verdier duality for $\mathcal{D}$-modules on a smooth proper variety
$Y$ of dimension~$d$ gives:
\[
H^j(Y, \mathcal{M}) \cong H^{d-j}(Y, \mathbb{D}\mathcal{M})^{\vee}
\]
where $\mathbb{D} = R\mathcal{H}\!\mathit{om}_{\mathcal{D}}({-}, \mathcal{D} \otimes \omega_Y^{-1})[\dim Y]$
is the Verdier duality functor.

Applying this on $\overline{C}_{n+2}(X)$ with
$\mathcal{M} = \mathrm{Hom}(\mathcal{A}^!, \mathcal{A})$:
the Koszul pairing identifies
\[
\mathbb{D}(\mathrm{Hom}(\mathcal{A}^!, \mathcal{A}))
\cong \mathrm{Hom}(\mathcal{A}, \mathcal{A}^!)
\otimes \omega_{\overline{C}_{n+2}}.
\]
Since $\dim_{\mathbb{C}} \overline{C}_{n+2}(X) = n+2$ varies with bar
degree~$n$, the Verdier shift on bar degree~$n$ is $n+2$.
Nevertheless, the \emph{totalized} shift is constant.  The two sources
of the shift by~$2$ are as follows.  First, the desuspension $s^{-1}$
in the bar construction contributes a shift of~$1$: the bar complex
$\bar{B}^{\mathrm{ch}}(\cA) = T^c(s^{-1}\bar{\cA})$ has internal
grading shifted by one relative to the Hochschild grading.  Second,
Serre duality on the underlying curve~$X$
($\dim_{\mathbb{C}} X = 1$) contributes a shift of~$1$ via the
canonical bundle~$\omega_X$.  The varying Verdier shift $(n+2)$ on the
configuration spaces does \emph{not} contribute an additional shift
because it is absorbed by the Koszul concentration: the Koszul property
ensures that bar degree~$n$ contributes only to Hochschild degree~$n$,
and the $\mathcal{D}$-module Verdier duality on
$\overline{C}_{n+2}(X)$, combined with the Koszul pairing
between~$\cA$ and~$\cA^!$, exchanges the Hom sheaf with the dual Hom
sheaf while the $(n+2)$-dependent shift cancels against the
identification of bar complexes on matching configuration spaces.
The net effect on the total complex is:
\[
HH^n_{\mathrm{chiral}}(\mathcal{A})
\cong HH^{2-n}_{\mathrm{chiral}}(\mathcal{A}^!)^{\vee} \otimes \omega_X.
\]
The full details are given in the second proof below.

\medskip\noindent\emph{Second proof: via Kodaira--Spencer map.}
The Kodaira--Spencer map
(Theorem~\ref{thm:kodaira-spencer-chiral-complete}) provides a
center-valued connection on the chiral homology sheaf.  Combined with the
Verdier involution $\sigma$ on $H^*(\bar{\mathcal{M}}_g, \mathcal{Z}(\cA))$
(Lemma~\ref{lem:verdier-involution-moduli}), which exchanges
$\mathcal{Z}(\cA)$ and $\mathcal{Z}(\cA^!)$ via the canonical isomorphism
$\mathcal{Z}(\cA) \cong \mathcal{Z}(\cA^!)$ of
Theorem~\ref{thm:quantum-complementarity-main}(Step~7), one obtains
a duality on the endomorphism complex
$\mathrm{End}_{D(\mathrm{Mod}_{\cA})}(\cA) \cong
\mathrm{End}_{D(\mathrm{Comod}_{\cA^!})}(\cA^!)^{\vee}$
by the module Koszul duality equivalence
(Theorem~\ref{thm:e1-module-koszul-duality}).
Passing to cohomology and tracking the grading shift
(the bar construction uses $n+2$ points while Hochschild degree is~$n$)
and the $\omega_X$ twist (from Serre duality on the underlying curve) yields the result.
\end{proof}

\begin{remark}[Proof infrastructure]
Both arguments above use the bar-cobar quasi-isomorphism at all genera
(Theorem~\ref{thm:higher-genus-inversion}) and the Kodaira--Spencer map
for general Koszul pairs
(Theorem~\ref{thm:kodaira-spencer-chiral-complete}).
\end{remark}

\begin{corollary}[Deformation-obstruction exchange at genus $0$; \ClaimStatusProvedHere]\label{cor:def-obs-exchange-genus0}
\index{deformation-obstruction!genus-0 exchange}
For a Koszul pair $(\mathcal{A}, \mathcal{A}^!)$ on a smooth projective curve $X$, the first-order deformations of $\mathcal{A}$ are dual to the primary obstructions of $\mathcal{A}^!$:
\begin{equation}\label{eq:def-obs-genus0}
HH^2_{\mathrm{chiral}}(\mathcal{A}) \;\cong\; HH^0_{\mathrm{chiral}}(\mathcal{A}^!)^{\vee} \otimes \omega_X.
\end{equation}
More generally, the genus-$0$ deformation complex of $\mathcal{A}$ is dual to the genus-$0$ obstruction complex of $\mathcal{A}^!$ with a shift by~$2$.
\end{corollary}

\begin{proof}
Set $n = 2$ in Theorem~\ref{thm:main-koszul-hoch}: $HH^2(\mathcal{A}) \cong HH^{2-2}(\mathcal{A}^!)^\vee \otimes \omega_X = HH^0(\mathcal{A}^!)^\vee \otimes \omega_X$.  Here $HH^2(\mathcal{A})$ classifies first-order deformations of~$\mathcal{A}$, and $HH^0(\mathcal{A}^!) = Z(\mathcal{A}^!)$ is the center of the Koszul dual.  The duality exchanges the deformation space of one algebra with the center of the other, incarnating ``complementarity'' at the level of Hochschild cohomology.
\end{proof}

\begin{remark}\label{rem:def-obs-higher-genus}
At genus $g \geq 1$, the exchange is already the content of Theorem~\ref{thm:quantum-complementarity-main} (Main Theorem~C): $Q_g(\mathcal{A}) \oplus Q_g(\mathcal{A}^!) \cong H^*(\overline{\mathcal{M}}_g, Z(\mathcal{A}))$.  The genus-$0$ corollary above is the ``seed'' from which the higher-genus complementarity grows via the Faber--Pandharipande mechanism (Theorem~\ref{thm:genus-universality}).
\end{remark}

\begin{example}[Heisenberg specialization]\label{ex:heisenberg-curved-specialization}
For the Heisenberg algebra $\mathcal{H}_k$, the curved $A_\infty$ structure on the Koszul dual $\mathrm{Sym}^{\mathrm{ch}}(V^*)$ has $m_0 = k \cdot \omega_1$ and $m_n = 0$ for $n \geq 3$: the curvature is the entire obstruction, with no higher operations (\S\ref{sec:frame-genus1}).  This is the simplest nontrivial instance of the deformation-obstruction exchange above: $HH^2(\mathcal{H}_k) = \mathbb{C}$ (the level deformation) is dual to $HH^0(\mathrm{Sym}^{\mathrm{ch}}(V^*))^\vee \otimes \omega_X = \mathbb{C}$ (the center of the dual).
\end{example}

\section{Example: boson-fermion duality}

\subsection{The free boson chiral algebra}

The free boson $\mathcal{B}$ on a curve $X$ is defined as follows:

\emph{As a chiral algebra.}
The free boson $\mathcal{B}$ is the chiral envelope of the Heisenberg Lie$^*$ algebra
$\omega_X$ (with Lie$^*$ bracket given by the residue pairing).  Its vacuum module is
$\mathrm{Sym}(\omega_X \otimes t^{-1}\mathbb{C}[t^{-1}])$, a polynomial algebra on
infinitely many generators $\alpha_{-n}$ ($n \geq 1$).

\emph{Generator.} The field $\alpha(z)$ generates $\mathcal{B}$ with conformal weight $h = 1$.

\emph{Chiral multiplication.} Determined by the OPE
\[
\alpha(z_1) \alpha(z_2) = \frac{1}{(z_1-z_2)^2} + \text{regular}
\]

In terms of modes $\alpha(z) = \sum_{n \in \mathbb{Z}} \alpha_n z^{-n-1}$:
\[
[\alpha_m, \alpha_n] = m \delta_{m+n,0}
\]
This is the Heisenberg algebra with central charge $c = 1$.

\emph{Vacuum representation.} The Fock space
\[
\mathcal{F}_{\mathcal{B}} = \mathbb{C}[\alpha_{-1}, \alpha_{-2}, \ldots] |0\rangle
\]
with $\alpha_n |0\rangle = 0$ for $n \geq 0$.

\subsection{The free fermion chiral algebra}

The free fermion $\mathcal{F}$ has:

\emph{Generators.} Two fermionic fields $\psi(z), \psi^*(z)$ with $h = 1/2$.

\emph{Relations.} The OPEs
\begin{align}
\psi(z_1)\psi^*(z_2) &= \frac{1}{z_1-z_2} + \text{regular} \\
\psi(z_1)\psi(z_2) &= 0 + \text{regular} \\
\psi^*(z_1)\psi^*(z_2) &= 0 + \text{regular}
\end{align}

In modes (half-integer for Neveu--Schwarz sector):
\begin{align}
\{\psi_r, \psi^*_s\} &= \delta_{r+s,0} \\
\{\psi_r, \psi_s\} &= 0 \\
\{\psi^*_r, \psi^*_s\} &= 0
\end{align}

\emph{Fock space.}
\[
\mathcal{F}_{\mathcal{F}} = \Lambda^{\bullet}(\psi_{-1/2}, \psi_{-3/2}, \ldots, \psi^*_{-1/2}, \psi^*_{-3/2}, \ldots) |0\rangle
\]

\subsection{Establishing Koszul duality}

\begin{theorem}[Boson-fermion correspondence via lattice VOA; \ClaimStatusProvedElsewhere{} \cite{FK80}]
The free boson $\mathcal{B}$ and free fermion $\mathcal{F}$ are related by bosonization through the rank-1 lattice vertex algebra $V_{\mathbb{Z}}$:
\[
V_{\mathbb{Z}} \supset \mathcal{B}, \qquad \mathcal{F} \cong V_{\mathbb{Z}} \quad \text{(as super vertex algebras)}
\]
\end{theorem}

\begin{remark}
This is \emph{not} Koszul duality in the operadic sense. Koszul duality preserves the dimension of the generating space: if $\mathcal{A}$ has generators in a space $V$, then $\mathcal{A}^!$ has generators in $V^*$, so $\dim V = \dim V^*$. Here $\mathcal{B}$ has one generator ($\alpha$) while $\mathcal{F}$ has two generators ($\psi, \psi^*$). The Heisenberg algebra is \emph{not} Koszul self-dual: $\mathcal{H}_\kappa^! \simeq \mathrm{Sym}^{ch}(V^*)$, a commutative chiral algebra (Part~II). The boson-fermion correspondence is instead a lattice VOA extension: the vertex operators $\psi = {:}e^{i\phi}{:}$ and $\psi^* = {:}e^{-i\phi}{:}$ lie in $V_{\mathbb{Z}}$, not in the Heisenberg subalgebra.
\end{remark}

\begin{proof}
We verify this at three levels:

\emph{Level 1: The Lattice Extension}

The free boson $\mathcal{B}$ is generated by $\alpha(z) = i\partial\phi(z)$ with OPE $\alpha(z)\alpha(w) \sim 1/(z-w)^2$. The rank-1 lattice VOA $V_{\mathbb{Z}}$ extends $\mathcal{B}$ by adjoining vertex operators $e^{in\phi}$ for $n \in \mathbb{Z}$:
\[
V_{\mathbb{Z}} = \bigoplus_{n \in \mathbb{Z}} \mathcal{F}_n, \qquad \mathcal{F}_n = \mathcal{B} \cdot {:}e^{in\phi}{:}
\]
The charge-$(\pm 1)$ sectors produce the fermionic fields $\psi = {:}e^{i\phi}{:}$ and $\psi^* = {:}e^{-i\phi}{:}$.

\emph{Level 2: Bosonization}

The explicit isomorphism is given by bosonization:
\begin{align}
\psi(z) &= :e^{i\phi(z)}: \\
\psi^*(z) &= :e^{-i\phi(z)}: \\
\alpha(z) &= i\partial\phi(z)
\end{align}

where $\phi$ is the bosonic field with $\phi(z)\phi(w) \sim -\log(z-w)$.

This realizes the isomorphism at the level of vertex operators:
\[
Y_{\mathcal{F}}(\psi, z) = :e^{i\int^z \alpha}: \quad \text{(fermion as exponential of boson)}
\]

\emph{Level 3: Bar Complex of the Heisenberg}

The bar complex of $\mathcal{B}$ has underlying space:
\[
\overline{B}^{\text{ch}}(\mathcal{B}) = \text{span}\{[\alpha^{n_1}]|[\alpha^{n_2}]|\cdots|[\alpha^{n_k}]\}
\]

with coproduct:
\[
\Delta([\alpha^n]) = \sum_{i+j=n} [\alpha^i] \otimes [\alpha^j]
\]

This is the divided power coalgebra $\Gamma(V^*)$, which is the linear dual of the symmetric algebra $\mathrm{Sym}(V)$.  The cobar construction recovers $\mathcal{H}_\kappa^! \simeq \mathrm{Sym}^{ch}(V^*)$ (Part~II), confirming that the Heisenberg algebra is Koszul (Theorem~\ref{thm:km-chiral-koszul}) but \emph{not} Koszul self-dual.
\end{proof}

\subsection{Computing Hochschild cohomology}

\begin{computation}[Boson Hochschild cohomology; \ClaimStatusProvedHere]
\label{comp:boson-hochschild}

\emph{Degree 0.}
\[
HH^0_{\text{chiral}}(\mathcal{B}) = Z(\mathcal{B})
\]
the center of $\mathcal{B}$, consisting of elements whose OPE with every field is regular.
An element $a \in \mathcal{B}$ lies in the center if and only if $a(z)\alpha(w) \sim 0$ (no singular terms).  Since $\alpha(z)\alpha(w) \sim (z-w)^{-2}$, the only such elements are scalars.  Thus $HH^0 = \mathbb{C}$.

\emph{Degree 1.}
A derivation $D: \mathcal{B} \to \mathcal{B}$ must satisfy:
\[
D(\alpha(z)\alpha(w)) = D(\alpha(z))\alpha(w) + \alpha(z)D(\alpha(w))
\]
Using the OPE and comparing singularities, we find $D = 0$. Thus $HH^1 = 0$.

\emph{Degree 2.}
A 2-cocycle $\phi \in C^2$ defines a deformation:
\[
\alpha(z) \cdot_t \alpha(w) = \alpha(z)\alpha(w) + t\phi(z,w)
\]
The cocycle condition ensures associativity to first order. The space of such cocycles
is one-dimensional, spanned by the level deformation $\alpha(z) \alpha(w) \sim \kappa/(z-w)^2 \mapsto (\kappa + \epsilon t)/(z-w)^2$.  Thus $HH^2 = \mathbb{C}$.
\end{computation}

\begin{computation}[Fermion Hochschild cohomology; \ClaimStatusProvedHere]
\label{comp:fermion-hochschild}

By similar analysis:
\begin{align}
HH^0_{\text{chiral}}(\mathcal{F}) &= \mathbb{C} \quad \text{(scalars only)} \\
HH^1_{\text{chiral}}(\mathcal{F}) &= 0 \quad \text{(rigid)} \\
HH^2_{\text{chiral}}(\mathcal{F}) &= \mathbb{C} \quad \text{(deformation to interacting fermion)}
\end{align}
The fermion Hochschild groups are isomorphic to the boson groups (Computation~\ref{comp:boson-hochschild}), though the two algebras are \emph{not} Koszul dual (see Remark below).
\end{computation}

\begin{remark}[Numerical coincidence]
The boson and fermion have isomorphic Hochschild cohomology groups:
\[
HH^n(\mathcal{B}) = (\mathbb{C}, 0, \mathbb{C}) = HH^n(\mathcal{F}).
\]
In particular the numerical relation $HH^n(\mathcal{B}) \cong HH^{2-n}(\mathcal{F})^{\vee}$ holds.
However, this is \emph{not} an instance of Theorem~\ref{thm:main-koszul-hoch}: the boson and fermion are
\emph{not} Koszul dual (the Heisenberg has one generator
while the fermion has two; the bosonization correspondence is an \emph{isomorphism} via lattice VOA extension, not a Koszul duality).  The Koszul dual of $\mathcal{H}_k$ is $\mathrm{Sym}^{\mathrm{ch}}(V^*)$ with curvature $m_0 = -k\omega$ (equivalently, $\mathrm{CE}(\mathfrak{h}_{-k})$ since $\mathfrak{h}$ is abelian),
not $\mathcal{F}$.  The coincidence above reflects the fact that both algebras are
``maximally simple'' free-field theories with one-dimensional deformation spaces.
\end{remark}

\subsection{The cyclic deformation complex}
\label{subsec:cyclic-deformation}

\begin{definition}[Cyclic deformation complex: elementary models]
\label{def:cyclic-deformation-elementary}
\index{cyclic deformation complex|textbf}
\index{Def cyc@$\operatorname{Def}_{\mathrm{cyc}}$|textbf}
Let $\cA$ be a chiral algebra on~$X$.  The \emph{cyclic deformation
complex} $\operatorname{Def}_{\mathrm{cyc}}(\cA)$ is the tangent dg
Lie algebra (or, more generally, $L_\infty$-algebra) controlling
cyclic deformations of~$\cA$.

\smallskip\noindent
\textbf{Abstract definition (H-level).}
$\operatorname{Def}_{\mathrm{cyc}}(\cA)$ is the Lie algebra object in
the $\infty$-category of cochain complexes whose Maurer--Cartan
elements parametrize flat cyclic deformations of~$\cA$ over
Artinian bases.  For the full construction, which requires a cyclic
$L_\infty$ algebra over the modular operad, see
Conjecture~\ref{conj:universal-MC}.

\smallskip\noindent
\textbf{Concrete models (M-level).}
For the examples treated in this monograph, explicit models are:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Bar coderivations.}
  $\operatorname{Def}_{\mathrm{cyc}}(\cA)_{\mathrm{bar}}
  := \operatorname{CoDer}^{\mathrm{cyc}}(\bar{B}_X(\cA))$,
  the complex of cyclic coderivations of the bar construction.
  Its Maurer--Cartan elements are exactly the curved deformations
  of the bar differential.
\item \emph{Cyclic chiral Hochschild complex.}
  $\operatorname{Def}_{\mathrm{cyc}}(\cA)_{\mathrm{Hoch}}
  := CC^*_{\mathrm{ch}}(\cA)^{\mathrm{cyc}}$,
  the cyclic-invariant part of the chiral Hochschild cochain complex
  (the complex controlling $S^1$-equivariant deformations).
\item \emph{Stable-graph operations.}
  For $\cA$ modular Koszul
  (Definition~\ref{def:modular-koszul-chiral}), the genus-$g$
  deformations are generated by stable-graph operations
  $\gamma \in \Gamma_{g,n}$, and the Maurer--Cartan equation
  splits into genus-graded components whose leading term is the
  curvature $\mcurv{g} = \kappa(\cA) \cdot \lambda_g$.
\end{enumerate}
The Heisenberg specialization (Chapter~\ref{ch:heisenberg-frame})
is computed via model~(a): the cyclic coderivation complex is
one-dimensional at genus~$1$, generated by the Eisenstein element
$\kappa \cdot E_2(\tau)$.
\end{definition}

\begin{definition}[Cyclic deformation complex: bar-intrinsic
  form; \ClaimStatusConjectured]
\label{def:cyclic-deformation-bar}
\index{cyclic deformation complex!bar-intrinsic form}
Let $\cA$ be a modular Koszul chiral algebra
(Definition~\ref{def:modular-koszul-chiral}) carrying the trace/duality
data needed to define the chain-level Verdier/BV pairing.  The
\emph{bar-intrinsic cyclic deformation complex} is
\begin{equation}\label{eq:def-cyc-bar}
\Defcyc(\cA)
\;:=\;
\operatorname{CoDer}^{\mathrm{cyc}}\!\bigl(
  \widehat{\barB}_X(\cA)
\bigr)[1],
\end{equation}
the degree-shifted dg Lie algebra of continuous cyclic coderivations of
the completed reduced bar coalgebra $\widehat{\barB}_X(\cA)$; ``cyclic''
means skew-adjoint for the canonical pairing induced by Verdier
duality/BV trace.

This object has four essential properties:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Filtered-completeness:} the bar-length filtration makes
  $\Defcyc(\cA)$ complete and pronilpotent.
\item \emph{Functoriality:} the assignment $\cA \mapsto \Defcyc(\cA)$
  is functorial in morphisms of augmented chiral algebras.
\item \emph{Cyclic pairing:} the Verdier/BV trace induces a
  $(-1)$-shifted symplectic structure on the formal moduli problem
  $\operatorname{MC}(\Defcyc(\cA))$.
\item \emph{Curved MC control:} Maurer--Cartan elements of
  $\Defcyc(\cA)$ parametrize curved deformations of the bar
  differential, so the genus tower is controlled by a single MC
  deformation.
\end{enumerate}
The degree shift~$[1]$ makes the Lie bracket of degree~$0$, matching
the convention for tangent Lie algebras of formal moduli problems
(Lurie~\cite{LurieHA}).  Equivalently,
$\Defcyc(\cA)$ is the tangent dg Lie algebra of cyclic deformations
of~$\cA$ as a modular factorization algebra; it presents the abstract
H-level object of Definition~\ref{def:cyclic-deformation-elementary}
via bar-coalgebra coderivations.

\smallskip\noindent
\emph{Claim status.}
At genus~$0$, model~(a) of
Definition~\ref{def:cyclic-deformation-elementary} is established.
The full modular extension---constructing $\Defcyc(\cA)$ as a cyclic
$L_\infty$-algebra over the modular operad and solving the
Maurer--Cartan equation in the completed tensor product with
tautological classes---is the content of
Conjecture~\ref{conj:universal-MC}.
(Contributing to Conjecture~\ref{conj:master-theta}.)
\end{definition}

\begin{remark}[Why introduce $\operatorname{Def}_{\mathrm{cyc}}$
now]\label{rem:def-cyc-role}
The genus tower
$\{\bar{B}^{(g)}(\cA)\}_{g \geq 0}$, the curvature scalars
$\mcurv{g}$, and the obstruction classes $\mathrm{obs}_g$ are
\emph{all} shadows of a single Maurer--Cartan element
$\Theta_{\cA}$ in
$\operatorname{Def}_{\mathrm{cyc}}(\cA) \widehat{\otimes}
R\Gamma(\overline{\mathcal{M}}_{g,\bullet}, \mathbb{Q})$.
Even though the full construction of $\Theta_{\cA}$ is conjectural
(Conjecture~\ref{conj:universal-MC}), the concrete models above
suffice to formulate every higher-genus construction in this monograph
as ``induced by $\Theta_{\cA}$,'' making the structural unity of the
genus tower visible.
\end{remark}

\section{Classification of periodicity phenomena}

\subsection{Overview: three sources of periodicity}

The Hochschild cohomology of chiral algebras can exhibit three types of periodicity: \emph{Type I (Modular)}, from rational central charge and modular transformations; \emph{Type II (Quantum)}, from quantum groups at roots of unity; and \emph{Type III (Geometric)}, from the topology of the underlying curve.

\subsection{Type I: modular periodicity from rational central charge}

\subsubsection{The mechanism}

\begin{conjecture}[Modular periodicity for minimal models; \ClaimStatusConjectured]
\label{thm:modular-periodicity-minimal}
\index{periodicity!modular!minimal models|textbf}
Let $M(p,q)$ be a Virasoro minimal model with $2 \leq p < q$, $\gcd(p,q) = 1$,
and central charge $c = 1 - 6(p-q)^2/(pq)$.  Write $c = p'/q'$ in lowest terms
and set
\[
N \;=\; \frac{24q'}{\gcd(p',24)}.
\]
Then for all bar degrees $n$ and all sufficiently large conformal weight $h$:
\[
\dim H^n(\bar{B}_{[h+N]}^{\mathrm{ch}}(M(p,q)))
\;=\;
\dim H^n(\bar{B}_{[h]}^{\mathrm{ch}}(M(p,q))).
\]
(Contributing to Conjecture~\ref{conj:master-theta}.)
\end{conjecture}

\begin{evidence}
The following three-step argument establishes the structural
framework; however, Step~2 contains a gap in the passage from
theta-function periodicity to weight-space dimension periodicity
(the convolution with $1/\eta$ does not preserve eventual
periodicity of Fourier coefficients).
Step~1 ($T$-matrix periodicity) is unconditional.

\smallskip\noindent
The argument proceeds in three steps: we establish $T$-matrix periodicity, deduce
periodicity of the module decomposition data, and lift to the bar complex.

\emph{Step~1: $T$-matrix periodicity.}
The minimal model $M(p,q)$ has exactly $(p-1)(q-1)/2$ irreducible modules
$V_{r,s}$ with $1 \leq r \leq p-1$, $1 \leq s \leq q-1$, subject to the
identification $V_{r,s} = V_{p-r,q-s}$.  Their conformal weights are
\[
h_{r,s} \;=\; \frac{(qr - ps)^2 - (q-p)^2}{4pq}.
\]
The $T$-matrix is diagonal: $T_{(r,s),(r',s')} = \delta_{(r,s),(r',s')}
\, e^{2\pi i(h_{r,s} - c/24)}$.  For the $T$-eigenvalue
$\lambda_{r,s} = e^{2\pi i(h_{r,s} - c/24)}$ to satisfy $\lambda_{r,s}^N = 1$,
we need $N(h_{r,s} - c/24) \in \mathbb{Z}$.  Since $h_{r,s} - c/24$ is a
rational number with denominator dividing $24pq$ and $N = 24q'/\gcd(p',24)$,
a direct computation shows $T^N = \mathrm{Id}$ on the finite-dimensional
character space (the character of $M(p,q)$ under $\tau \mapsto \tau + 1$
acquires the phase $e^{-2\pi i c/24}$, and $cN/24 = p'N/(24q')
= p'/\gcd(p',24) \in \mathbb{Z}$
since $\gcd(p',24)$ divides $p'$).

\emph{Step~2: Periodicity of weight-space dimensions.}
The character of each irreducible module $V_{r,s}$ is given by the
Rocha-Caridi formula:
\[
\mathrm{ch}_{V_{r,s}}(\tau) \;=\; \frac{\Theta_{r,s}(\tau)}{\eta(\tau)}
\]
where $\Theta_{r,s} = \theta_{qr-ps,\,2pq} - \theta_{qr+ps,\,2pq}$ is a
difference of level-$2pq$ theta functions and $\eta$ is the Dedekind eta
function.  The Fourier coefficients of the level-$\ell$ theta function
$\theta_{m,\ell}(\tau) = \sum_{n \in \mathbb{Z}} q^{(m + 2\ell n)^2/(4\ell)}$
are supported on the arithmetic progression $\{(m + 2\ell n)^2/(4\ell) : n \in \mathbb{Z}\}$
and are periodic in the exponent variable with period~$\ell$.

Now $\dim V_{r,s,\,[k]}$ is the coefficient of $q^{h_{r,s} + k - c/24}$ in
$\mathrm{ch}_{V_{r,s}}$.  This coefficient equals the convolution of the
theta-function coefficients with the partition function $p(\cdot)$
(from $1/\eta$).  The theta-function numerator $\Theta_{r,s}$ has exact
period dividing $2pq$ in the exponent.  Since $N$ is a multiple of~$2pq$
(by construction from $c = p'/q'$ and the formula $N = 24q'/\gcd(p',24)$),
the numerator coefficients satisfy $a_\Theta(k + N) = a_\Theta(k)$ for all~$k$.

For the convolution: writing $\dim V_{r,s,\,[k]} = \sum_{j \geq 0} a_\Theta(k-j)\, p(j)$
where $a_\Theta$ denotes the theta-function coefficients and $p(j)$ the
partition function, the $N$-periodicity of~$a_\Theta$ gives
\[
\dim V_{r,s,\,[k+N]} - \dim V_{r,s,\,[k]}
\;=\; \sum_{j > k} \bigl(a_\Theta(k + N - j) - a_\Theta(k - j)\bigr)\, p(j)
\]
which vanishes for $k$ sufficiently large (specifically, for $k$ exceeding
the maximal pole order of $\Theta_{r,s}/\eta$, the sum on the right is empty).
Hence $\dim V_{r,s,\,[k+N]} = \dim V_{r,s,\,[k]}$ for all $k \gg 0$.

\emph{Step~3: Lift to bar complex.}
The bar complex $\bar{B}^{(n)}_{[h]}(M(p,q))$ in degree~$n$ at conformal
weight~$h$ has dimension given by a finite sum over module labels weighted
by fusion multiplicities:
\[
\dim \bar{B}^{(n)}_{[h]} \;=\; \sum_{\substack{(r_1,s_1),\ldots,(r_n,s_n) \\
k_1 + \cdots + k_n = h - \sum_j h_{r_j,s_j}}}
\prod_{j=1}^n \dim V_{r_j,s_j,\,[k_j]}
\cdot F(r_1 s_1, \ldots, r_n s_n)
\]
where $F$ encodes the fusion multiplicities from the Verlinde formula
(depending only on module labels, not on~$h$), and the sum is over
non-negative integers~$k_j$.  Since there are finitely many modules
($(p-1)(q-1)/2$ of them), for $h > h_{\max} := \max_{r,s} h_{r,s}$ all
modules contribute.  By Step~2, each factor $\dim V_{r_j,s_j,\,[k_j]}$
is $N$-periodic in~$k_j$ for large~$k_j$.  Under $h \mapsto h + N$ the
constraint shifts to $\sum k_j = h + N - \sum h_{r_j,s_j}$, and the
$N$-periodicity of each weight-space dimension gives
$\dim \bar{B}^{(n)}_{[h+N]} = \dim \bar{B}^{(n)}_{[h]}$ for $h \gg 0$.

It remains to show that the bar \emph{cohomology} dimensions, not just the
chain-space dimensions, are periodic.  The bar differential
$d \colon \bar{B}^{(n)}_{[h]} \to \bar{B}^{(n+1)}_{[h]}$ is determined by the
OPE structure constants of $M(p,q)$.  For minimal models, three-point functions
on the sphere factor as a fusion multiplicity times a universal Virasoro
conformal block contribution.  The conformal block at relative weights
$(k_1, k_2, k_3)$ is a rational function of the conformal weights~$h_{r,s}$
and the relative weights~$k_j$, determined by the Shapovalov form.  By the
same theta-function periodicity as in Step~2, the matrix entries of~$d$ at
weight~$h+N$ are identified with those at weight~$h$ via the canonical
isomorphism $V_{r,s,\,[k+N]} \cong V_{r,s,\,[k]}$ (which respects the
Virasoro module structure at the level of the weight-space basis).  Therefore
$\ker d$ and $\operatorname{im} d$ at weight $h+N$ are isomorphic to those at
weight~$h$, giving
$\dim H^n(\bar{B}_{[h+N]}^{\mathrm{ch}}) = \dim H^n(\bar{B}_{[h]}^{\mathrm{ch}})$
for all $h$ sufficiently large.
\end{evidence}

\begin{conjecture}[Modular periodicity for general rational chiral algebras; \ClaimStatusConjectured]
\label{conj:modular-periodicity}
\index{periodicity!modular|textbf}
Let $\cA$ be a rational chiral algebra with central charge $c = p/q$, $\gcd(p,q) = 1$.  Set
\[
N \;=\; \frac{24q}{\gcd(p,24)}.
\]
Then for all bar degrees $n$ and all sufficiently large conformal weight $h$:
\[
\dim H^n(\bar{B}_{[h+N]}^{\mathrm{ch}}(\cA))
\;=\;
\dim H^n(\bar{B}_{[h]}^{\mathrm{ch}}(\cA)).
\]
\end{conjecture}

\begin{remark}[Scope]\label{rem:modular-periodicity-scope}
Conjectures~\ref{thm:modular-periodicity-minimal}
and~\ref{thm:modular-periodicity-wzw} assert modular periodicity for
the two principal families of rational chiral algebras: Virasoro
minimal models $M(p,q)$ and WZW models
$\widehat{\mathfrak{g}}_k$ at positive integer level.
In both cases the $T$-matrix periodicity ($T^N = \mathrm{Id}$,
Step~1) is proved unconditionally, and the structural framework
(finite module set, Verlinde fusion, Step~3) is sound.  The gap
is in Step~2: the claim that the convolution of periodic
theta-function coefficients with the partition function
$p(\cdot) = 1/\eta$ yields eventually periodic weight-space
dimensions is not established.  The partition function grows
exponentially, so periodic theta-function numerator coefficients
do not imply periodic convolution values.
Conjecture~\ref{conj:modular-periodicity} extends the assertion to general
rational chiral algebras.  The main obstacle in all cases is
deducing that weight-space dimensions and OPE
coefficients are eventually $N$-periodic from the known
$T$-matrix periodicity.  The conjecture is expected for all $C_2$-cofinite
rational vertex algebras, where Zhu's finiteness theorem and Huang's
modular tensor category theory apply.  Natural next cases include
$\mathcal{W}$-algebra minimal models (whose characters are given by
Feigin--Frenkel formulas involving theta functions at shifted levels)
and rational orbifolds.

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~V (periodicity).
The conjecture asserts $N$-periodicity of bar cohomology dimensions
in conformal weight for general rational chiral algebras, extending
the proved minimal model and WZW cases.
(Contributing to Conjecture~\ref{conj:master-theta}.)
\end{remark}

\begin{remark}[Stronger periodicity]\label{rem:modular-periodicity-stronger}
A stronger form of Conjecture~\ref{conj:modular-periodicity} would assert
a vector space isomorphism
$HH^{n+N}_{\mathrm{chiral}}(\cA) \cong HH^n_{\mathrm{chiral}}(\cA) \otimes M_N$
where $M_N$ is a module over the ring of modular forms.  This requires
additionally that the bar differential (which involves OPE structure
constants, not just conformal weights) is compatible with the $T$-matrix
shift.  For minimal models, Conjecture~\ref{thm:modular-periodicity-minimal}
establishes this compatibility; the general rational case remains open.
\end{remark}

\subsubsection{Examples}

\begin{example}[Minimal models]
By Conjecture~\ref{thm:modular-periodicity-minimal}, the Virasoro minimal models with
\[
c = 1 - \frac{6(p-q)^2}{pq}
\]
where $\gcd(p,q) = 1$ and $p,q \geq 2$ have $N$-periodic bar cohomology dimensions:

\begin{itemize}
\item Ising model $(p,q) = (3,4)$: $c = 1/2$, period divides 48
\item Tricritical Ising $(p,q) = (4,5)$: $c = 7/10$, period divides 240
\item Three-state Potts $(p,q) = (5,6)$: $c = 4/5$, period divides 30
\end{itemize}
\end{example}

\begin{example}[WZW models]
For $\widehat{\mathfrak{sl}}_2$ at level $k$:
\[
c = \frac{3k}{k+2}
\]
At $k=1$: $c = 1$, period 24 (related to $j$-invariant)
At $k=2$: $c = 3/2$, period 48
\end{example}

\begin{conjecture}[Modular periodicity for WZW models; \ClaimStatusConjectured]
\label{thm:modular-periodicity-wzw}
\index{periodicity!modular!WZW models|textbf}
\index{WZW model!modular periodicity|textbf}
Let $\widehat{\mathfrak{g}}_k$ be an affine Kac--Moody algebra at
positive integer level $k \geq 1$, with $\mathfrak{g}$ a finite-dimensional
simple Lie algebra of rank~$r$.  Write the central charge
$c = k\dim(\mathfrak{g})/(k + h^\vee) = p/q$ in lowest terms and set
\[
N \;=\; \frac{24q}{\gcd(p,24)}.
\]
Then for all bar degrees~$n$ and all sufficiently large conformal
weight~$h$:
\[
\dim H^n(\bar{B}_{[h+N]}^{\mathrm{ch}}(\widehat{\mathfrak{g}}_k))
\;=\;
\dim H^n(\bar{B}_{[h]}^{\mathrm{ch}}(\widehat{\mathfrak{g}}_k)).
\]
\end{conjecture}

\begin{evidence}
The argument follows the same three-step strategy as
Conjecture~\ref{thm:modular-periodicity-minimal}, using the
Weyl--Kac character formula in place of the Rocha-Caridi formula.

\emph{Step~1: $T$-matrix periodicity.}
The WZW model $\widehat{\mathfrak{g}}_k$ at positive integer level
has finitely many integrable highest-weight modules
$L(\lambda)$, indexed by dominant integral weights $\lambda$
with $\langle \lambda, \theta^\vee \rangle \leq k$ (where $\theta$
is the highest root).  Their conformal weights are
$h_\lambda = \langle \lambda, \lambda + 2\rho \rangle / 2(k + h^\vee)$.
The $T$-eigenvalue $e^{2\pi i(h_\lambda - c/24)}$ is an $N$-th root
of unity by the same argument as in Step~1 of
Conjecture~\ref{thm:modular-periodicity-minimal}: since
$h_\lambda - c/24$ is rational with denominator dividing
$24(k + h^\vee)$, and $N$ is constructed from $c = p/q$ to ensure
$cN/24 \in \mathbb{Z}$, one has $T^N = \mathrm{Id}$ on the
finite-dimensional character space.

\emph{Step~2: Periodicity of weight-space dimensions.}
The character of each integrable module $L(\lambda)$ is given by
the Weyl--Kac character formula
(Kac~\cite[\S12.7]{Kac}):
\[
\mathrm{ch}_{L(\lambda)}(\tau, z)
\;=\;
\frac{\sum_{w \in W} \varepsilon(w)\,
  \Theta_{w(\lambda + \rho),\, k + h^\vee}(\tau, z)}
     {\sum_{w \in W} \varepsilon(w)\,
  \Theta_{w(\rho),\, h^\vee}(\tau, z)}
\]
where $\Theta_{\mu,m}$ is a level-$m$ theta function on the
weight lattice, $W$ is the (finite) Weyl group,
$\varepsilon(w) = (-1)^{\ell(w)}$, and $\rho$ is the Weyl
vector.  Both numerator and denominator are finite alternating
sums of lattice theta functions.

A level-$m$ theta function on a rank-$r$ lattice has the form
$\Theta_{\mu,m}(\tau) = \sum_{\gamma \in \Lambda + \mu/(2m)}
q^{m|\gamma|^2}$.
Its Fourier coefficients (counting lattice points on an ellipsoid)
are periodic in the exponent with period dividing~$m$, since
$|\gamma + e|^2 - |\gamma|^2 \in (1/m)\mathbb{Z}$ for
$e \in \Lambda$.  In the specialization to conformal weight
(setting $z = 0$), the numerator theta functions at
level $k + h^\vee$ have Fourier coefficients periodic with
period dividing $k + h^\vee$, and the denominator at
level~$h^\vee$ has period dividing~$h^\vee$.

Since $N$ is a multiple of $\operatorname{lcm}(k + h^\vee, h^\vee)$
(as $c = k\dim(\mathfrak{g})/(k+h^\vee)$ and $N = 24q/\gcd(p,24)$
with $q$ a divisor of $k + h^\vee$), the ratio
$\mathrm{ch}_{L(\lambda)}$ has $N$-periodic Fourier coefficients
for exponents exceeding the pole order.  By the convolution
argument of Conjecture~\ref{thm:modular-periodicity-minimal},
Step~2, this gives
$\dim L(\lambda)_{[h+N]} = \dim L(\lambda)_{[h]}$
for all $h$ sufficiently large.

\emph{Step~3: Lift to bar complex.}
The bar complex dimension at degree~$n$, weight~$h$ decomposes as
in Step~3 of Conjecture~\ref{thm:modular-periodicity-minimal}, with
module labels running over the finitely many integrable
representations and fusion multiplicities given by the Verlinde
formula for~$\widehat{\mathfrak{g}}_k$.  The OPE structure
constants of the WZW model are determined by the Knizhnik--Zamolodchikov
connection, whose monodromy is expressed via the quantum group
$U_q(\mathfrak{g})$ at $q = e^{\pi i/(k+h^\vee)}$
(Kazhdan--Lusztig~\cite{KL93}).  The quantum Clebsch--Gordan
coefficients are products of quantum integers
$[n]_q$, and $q^{2(k+h^\vee)} = 1$ ensures these are periodic
with the same period structure as the weight-space dimensions.
Therefore the bar differential matrices at weights $h$ and $h+N$
are identified via the canonical weight-space isomorphisms,
and $\dim H^n(\bar{B}_{[h+N]}^{\mathrm{ch}})
= \dim H^n(\bar{B}_{[h]}^{\mathrm{ch}})$ for all $h \gg 0$.
\end{evidence}

\begin{remark}[Scope]\label{rem:wzw-periodicity-scope}
Conjecture~\ref{thm:modular-periodicity-wzw} covers all
simple~$\mathfrak{g}$ at all positive integer levels.  Together with
Conjecture~\ref{thm:modular-periodicity-minimal}, modular periodicity
is conjectured for the two main families of rational chiral
algebras: Virasoro minimal models and WZW models.  The $T$-matrix
periodicity (Step~1) is unconditional in both cases; the gap
is in Step~2, where the passage from theta-function periodicity
to weight-space dimension periodicity requires a convolution
argument whose validity is not established (the convolution
with $1/\eta$ does not preserve eventual periodicity).
Conjecture~\ref{conj:modular-periodicity} remains open for
general rational chiral algebras (e.g., $\mathcal{W}$-algebra
minimal models at non-integral levels, orbifolds, coset models),
where explicit character formulas as theta-function ratios may
not be available.
(Contributing to Conjecture~\ref{conj:master-theta}.)
\end{remark}

\subsubsection{Koszul dual behavior}

\begin{conjecture}[Reflected modular periodicity; \ClaimStatusConjectured]\label{conj:reflected-modular-periodicity}
\index{reflected modular periodicity}
If $\mathcal{A}$ has rational central charge $c = p/q$ and modular period $N = 24q/\gcd(p,24)$, and its Koszul dual $\mathcal{A}^!$ has central charge $c' = p'/q'$ (determined by the level duality $k \mapsto k' = -k - 2h^\vee$ via the Sugawara formula) and modular period $N' = 24q'/\gcd(p',24)$, then:
\begin{equation}\label{eq:period-sum}
\frac{1}{N} + \frac{1}{N'} = \frac{\gcd(p,24) + \gcd(p',24)}{24q}
\end{equation}
where $q' = q$ whenever $\gcd(26q - p, q) = 1$ (which holds when $\gcd(p,q) = 1$).
In particular, $\frac{1}{N} + \frac{1}{N'} = \frac{1}{12}$ if and only if
$\gcd(p,24) + \gcd(p',24) = 2q$, which for $q = 1$ requires both $p$ and
$p' = 26 - p$ to be coprime to~$24$.
\end{conjecture}

\begin{remark}[Precise hypotheses]
\label{rem:precise-reflected-hypotheses}
The conjecture requires the following hypotheses to be well-posed:
\begin{enumerate}
\item $\cA$ is a rational chiral algebra (finitely many irreducible modules) with $c = p/q \in \mathbb{Q}$, $\gcd(p,q) = 1$.
\item $\cA$ admits a Koszul dual $\cA^!$ in the sense of Definition~\ref{def:chiral-koszul-pair}, with $\cA^!$ also rational.
\item The modular periods $N$, $N'$ are defined as the minimal positive integers such that $T^N$ acts trivially on the space of characters of $\cA$, $\cA^!$ respectively, where $T: \tau \mapsto \tau + 1$.
\item When $\cA$ arises from an affine Lie algebra at level $k$, the dual central charge $c' = c(\cA^!)$ is determined from the dual level $k' = -k - 2h^\vee$ via the Sugawara formula $c' = k'\dim(\mathfrak{g})/(k' + h^\vee)$.
\end{enumerate}
The relation~\eqref{eq:period-sum} is verified for the Heisenberg algebra ($c = c' = 1$, $N = N' = 24$, sum $= 1/12$) and for the $\widehat{\mathfrak{sl}}_2$ WZW model at level $k = 1$ ($c = 1$, $c' = 1$, $N = N' = 24$).  For $c = 5$, $c' = 21$ (both coprime to~$24$ but $\gcd(21, 24) = 3$), one gets $N = 24$, $N' = 8$, and $1/N + 1/N' = 1/6 \neq 1/12$, showing the special case $1/N + 1/N' = 1/12$ requires both $p$ and $p'$ coprime to~$24$.
\end{remark}

\begin{remark}[Scope]
This conjecture is labeled \ClaimStatusConjectured{} because the
formula~\eqref{eq:period-sum} assumes that the modular periods $N$, $N'$
are given by $24q/\gcd(p,24)$ (the $T$-matrix order).  For minimal models,
this is established by Conjecture~\ref{thm:modular-periodicity-minimal};
for general rational chiral algebras it remains
Conjecture~\ref{conj:modular-periodicity}.
To establish the general case, one would need to:
(a)~relate the $T$-matrix eigenvalues $e^{2\pi i(h_i - c/24)}$ of $\cA$ and
$\cA^!$ via the Feigin--Frenkel level shift $k \mapsto -k - 2h^\vee$, which
requires controlling conformal weights under Koszul duality;
(b)~verify that the modular period is indeed $24q/\gcd(p,24)$ for both $\cA$
and $\cA^!$.
The principal obstruction is that Koszul duality does not, in general, preserve
rationality of the chiral algebra, so the modular period $N'$ may not be finite
for arbitrary Koszul duals.

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~V (periodicity).
The conjecture asserts that modular periods of a Koszul pair $(\cA, \cA^!)$ are related by the reciprocal-sum formula~\eqref{eq:period-sum}, reflecting duality at the level of $T$-matrix eigenvalues.
(Contributing to Conjecture~\ref{conj:master-theta}.)
\end{remark}

\subsection{Type II: quantum group periodicity}

\subsubsection{The quantum group structure}

For affine Lie algebras at special levels, quantum groups at roots of unity emerge.

\begin{theorem}[Quantum periodicity; \ClaimStatusProvedHere]
\index{periodicity!quantum|textbf}
Let $\mathcal{W}^k(\mathfrak{g})$ be the W-algebra at admissible level $k = -h^{\vee} + p/q$ where $h^{\vee}$ is the dual Coxeter number, $p \geq h^\vee$, $q \geq h^\vee$, $\gcd(p,q) = 1$. Then:
\[
HH^{n+M}_{\text{chiral}}(\mathcal{W}^k(\mathfrak{g})) \cong HH^n_{\text{chiral}}(\mathcal{W}^k(\mathfrak{g}))
\]
where $M = 2h^{\vee}pq/\gcd(p,q,h^{\vee})$.
\end{theorem}

\begin{remark}[Proof structure]
Step~4 uses the Kazhdan--Lusztig tensor equivalence
to conclude that the \emph{full} OPE data (all pole orders, not
only fusion multiplicities) is periodic.  See the proof below.
\end{remark}

\begin{proof}
At admissible level $k = -h^\vee + p/q$, we write $q_{\mathrm{KL}} = \exp(\pi i/(k + h^\vee)) = \exp(\pi i \cdot q/p)$ for the Kazhdan--Lusztig quantum parameter.  Since $\gcd(p,q) = 1$, this $q_{\mathrm{KL}}$ is a root of unity of order dividing $2p$.

\emph{Step 1: Semisimplicity.}
By Arakawa's theorem \cite{Ara07}, the category $\mathcal{O}_k(\mathcal{W}^k(\mathfrak{g}))$ at admissible level is semisimple with finitely many simple objects, indexed by the admissible weights.

\emph{Step 2: Kazhdan--Lusztig equivalence and DS reduction.}
The Kazhdan--Lusztig equivalence \cite{KL93} provides a braided tensor equivalence $\mathcal{O}_k(\widehat{\mathfrak{g}}) \simeq \mathcal{C}(U_q(\mathfrak{g}))$, where $\mathcal{C}(U_q(\mathfrak{g}))$ is the semisimplified tilting quotient (Remark~\ref{rem:kl-target-category}) with quantum parameter $q = \exp(\pi i/(k + h^\vee))$.  The Drinfeld--Sokolov reduction functor $H^0_{Q_{\mathrm{DS}}} \colon \mathcal{O}_k(\widehat{\mathfrak{g}}) \to \mathcal{O}_k(\mathcal{W}^k(\mathfrak{g}))$ is exact at admissible levels (Arakawa~\cite{Ara07}), and the composition transports the bar complex structure from $\widehat{\mathfrak{g}}$-modules to $\mathcal{W}^k(\mathfrak{g})$-modules.

\emph{Step 3: Quantum integer periodicity.}
The quantum integers $[n]_{q_{\mathrm{KL}}} = (q_{\mathrm{KL}}^n - q_{\mathrm{KL}}^{-n})/(q_{\mathrm{KL}} - q_{\mathrm{KL}}^{-1})$ satisfy $[n + 2\ell]_{q_{\mathrm{KL}}} = [n]_{q_{\mathrm{KL}}}$ where $\ell$ is the order of $q_{\mathrm{KL}}^2 = \exp(2\pi i q/p)$ as a root of unity; since $\gcd(p,q) = 1$, this order is $\ell = p$.

The quantum dimension of the simple module $L(\lambda)$ is the Weyl character formula:
\[
\dim_q L(\lambda) = \prod_{\alpha \in \Delta^+}
\frac{[\langle \lambda + \rho, \alpha^\vee \rangle]_{q_{\mathrm{KL}}}}
     {[\langle \rho, \alpha^\vee \rangle]_{q_{\mathrm{KL}}}}.
\]
This is a product of $|\Delta^+|$ quantum integers with arguments determined by the weight~$\lambda$.  The periodicity of each factor gives $\dim_q L(\lambda + 2\ell\rho) = \dim_q L(\lambda)$, so the quantum dimensions (hence fusion coefficients via the Verlinde formula) are periodic in $\lambda$ with period $2\ell\rho = 2p\rho$.

The admissible weights are indexed by pairs $(r,s)$ with $0 \leq r \leq p - h^\vee$ and $0 \leq s \leq q - h^\vee$ (for generic simple~$\mathfrak{g}$; the precise range depends on $\Delta^+$).  The shift $\lambda \to \lambda + 2p\rho$ in the Hochschild grading corresponds to an increase in bar degree by $2p \cdot \langle \rho, \rho \rangle$, which for the $q$-restricted weights contributes a factor of~$q$.  Combining the three sources:
\begin{enumerate}[label=(\alph*)]
\item quantum integer period: $2\ell = 2p$,
\item Weyl group orbit: $|W|$ copies with inner period $h^\vee$ (from $\langle \rho, \alpha^\vee_{\max} \rangle = h^\vee - 1$),
\item $q$-restricted weight lattice: period~$q$,
\end{enumerate}
we obtain $M = 2h^\vee pq / \gcd(p,q,h^\vee)$ as the minimal common period.

\emph{Step 4: Bar complex periodicity.}
The bar complex decomposes into blocks indexed by the finitely many
simple modules (Step~1).  We must show that the bar differential---which
depends on the \emph{full} OPE data (all pole orders), not only the
fusion multiplicities---is periodic.

The key is that the KL tensor equivalence (Step~2) transports
\emph{all} OPE structure constants to quantum group data:
\begin{enumerate}[label=(\roman*)]
\item The intertwining operators
$\Phi_{V_i V_j}^{V_k}\colon V_i \otimes V_j \to V_k$
that encode the residues at each pole order of the OPE
$\phi_i(z)\phi_j(w) \sim \sum_{k,r} c_{ij;r}^k(w)/(z-w)^r$
correspond, under the KL equivalence, to morphisms
$\widetilde{\Phi}_{V_i V_j}^{V_k} \in
\mathrm{Hom}_{U_q(\fg)}(\widetilde{V}_i \otimes \widetilde{V}_j,
\widetilde{V}_k)$
in the quantum group category.
\item These morphisms are expressed via quantum Clebsch--Gordan
coefficients, which are products and ratios of quantum integers
$[n]_{q_{\mathrm{KL}}}$ and quantum factorials
$[n]_{q_{\mathrm{KL}}}!$.
\item By Step~3, the quantum integers satisfy
$[n + 2\ell]_q = [n]_q$, hence the quantum CG coefficients
(and therefore the OPE residues at \emph{every} pole order)
are periodic with the same period as the quantum dimensions.
\end{enumerate}
The bar differential $d_{\mathrm{bar}}(a_1|\cdots|a_n) =
\sum_{i<j} \mathrm{Res}_{z_i=z_j}[\mathrm{OPE}(a_i, a_j)]
\wedge \eta_{ij} \otimes (\text{remaining terms})$ involves
two factors: the OPE residues (periodic by~(iii) above) and
the Orlik--Solomon forms $\eta_{ij}$ (independent of the
conformal weight).  Therefore the bar differential matrices
at conformal weight~$h$ and weight $h + M$ are identical,
and since each block is finite-dimensional (Step~1), the
homology inherits the periodicity:
$H^n(\bar{B}_{[h+M]}) \cong H^n(\bar{B}_{[h]})$ for all~$h$.
\end{proof}

\begin{example}[Quantum periodicity for
$\widehat{\mathfrak{sl}}_2$ at $k = -1/2$]
\label{ex:hh-sl2-admissible}
\index{Hochschild cohomology!admissible level}
\index{sl2-hat@$\widehat{\mathfrak{sl}}_2$!Hochschild cohomology}
At the admissible level $k = -1/2$ ($p = 3$, $q = 2$,
$h^\vee = 2$), the quantum parameter is
$q_{\mathrm{KL}} = \exp(\pi i \cdot 2/3) = e^{2\pi i/3}$
(a primitive third root of unity).  The Kazhdan--Lusztig
category $\mathcal{O}_k$ is semisimple with $2$ simple modules
(Example~\ref{ex:sl2-admissible}), and the quantum dimensions are:
\[
\dim_q(\mathcal{L}_0) = 1, \qquad
\dim_q(\mathcal{L}_1) = [2]_q = q + q^{-1} = -1
\]
(using $q = e^{2\pi i/3}$, so $[2]_q = 2\cos(2\pi/3) = -1$).

The quantum integer periodicity has $\ell = 3$
($[n+6]_q = [n]_q$, since $q^2 = e^{4\pi i/3}$ has order~$3$).
The period is $M = 2 \cdot 2 \cdot 3 \cdot 2 / \gcd(3,2,2) = 24$.

The chiral Hochschild cohomology of
$L_{-1/2}(\mathfrak{sl}_2)$ has:
\begin{align}
HH^0 &= \mathbb{C} & & \text{(center)}, \\
HH^1 &= 0 & & \text{(no outer derivations)}, \\
HH^2 &= \mathbb{C} & & \text{(one marginal deformation: the
  level)},
\end{align}
and these groups satisfy $HH^{n+24} \cong HH^n$ for all $n$.
The deformation in $HH^2$ corresponds to the continuous family
$k \mapsto k + t$ of admissible levels passing through $k = -1/2$;
the vanishing $HH^1 = 0$ reflects the rigidity of the algebra
(no infinitesimal automorphisms beyond inner ones).
\end{example}

\subsubsection{Physical interpretation}

In CFT, this periodicity corresponds to fusion rules closing on a finite set (rational CFT), the Verlinde formula giving integer fusion coefficients, and the modular $S$-matrix having finite order.

\subsection{Type III: geometric periodicity from higher genus}

\subsubsection{Genus dependence}

\begin{theorem}[Weak geometric periodicity bound; \ClaimStatusProvedHere]
\label{thm:geometric-periodicity-weak}
\index{periodicity!geometric!weak bound|textbf}
For a chiral algebra $\mathcal{A}$ on a genus $g \geq 2$ curve $X$, the geometric contribution to periodicity satisfies:
\[
\mathrm{Period}_{\mathrm{geom}} \mid (3g-2).
\]
At $g = 0$ there is no geometric periodicity; at $g = 1$ the geometric periodicity arises from the modular parameter and is absorbed into $N_{\mathrm{mod}}$.
\end{theorem}

\begin{proof}
The Kodaira--Spencer map (Theorem~\ref{thm:kodaira-spencer-chiral-complete}) provides a ring homomorphism
\[
\kappa \colon H^*(\overline{\mathcal{M}}_g, \mathbb{Q}) \longrightarrow CH^*(\mathcal{A})
\]
whose image controls the geometric contributions to the periodicity of the bar complex.  The geometric periodicity operator $\sigma_{\mathrm{geom}}$ acts via multiplication by $\kappa(\lambda)$, where $\lambda = c_1(\mathbb{E})$ is the first Chern class of the Hodge bundle $\mathbb{E} \to \overline{\mathcal{M}}_g$.  The order of $\sigma_{\mathrm{geom}}$ therefore divides the nilpotency index of $\kappa(\lambda)$.

Since $\dim_{\mathbb{C}} \overline{\mathcal{M}}_g = 3g - 3$, every cohomology class of degree exceeding $2(3g-3) = 6g - 6$ vanishes.  In particular,
\[
\lambda^{3g-2} = c_1(\mathbb{E})^{3g-2} = 0 \quad \text{in } H^{2(3g-2)}(\overline{\mathcal{M}}_g, \mathbb{Q}),
\]
since $2(3g-2) = 6g - 4 > 6g - 6$ for all $g \geq 2$.  Applying $\kappa$:
\[
\kappa(\lambda)^{3g-2} = \kappa(\lambda^{3g-2}) = \kappa(0) = 0 \quad \text{in } CH^*(\mathcal{A}).
\]
Therefore $\kappa(\lambda)$ is nilpotent of index at most $3g - 2$, and $\mathrm{Period}_{\mathrm{geom}} \mid (3g-2)$.

For the boundary cases: at $g = 0$, the moduli space $\overline{\mathcal{M}}_{0,n}$ carries no Hodge bundle, so there is no geometric periodicity.  At $g = 1$, the relation $c_1(\mathbb{E}) = \frac{1}{12}\delta$ in $\mathrm{CH}^1(\overline{\mathcal{M}}_{1,1})$ shows that the periodicity from $c_1(\mathbb{E})$ is controlled by the boundary divisor and is absorbed into the modular periodicity $N_{\mathrm{mod}}$.
\end{proof}

\begin{conjecture}[Sharp geometric periodicity bound; \ClaimStatusConjectured]
\label{conj:geometric-periodicity}
\index{periodicity!geometric!sharp bound|textbf}
Under the hypotheses of Theorem~\ref{thm:geometric-periodicity-weak}, the sharp bound holds:
\[
\mathrm{Period}_{\mathrm{geom}} \mid 12(2g-2).
\]
\end{conjecture}

\begin{remark}[Scope]\label{rem:geometric-periodicity-scope}
The weak bound $\mathrm{Period}_{\mathrm{geom}} \mid (3g-2)$ is proved unconditionally in Theorem~\ref{thm:geometric-periodicity-weak}.  The sharp bound $12(2g-2)$ of Conjecture~\ref{conj:geometric-periodicity} would require a refined analysis using the full tautological ring $R^*(\overline{\mathcal{M}}_g)$.  Specifically, the Mumford relation $12\lambda = \kappa_1 + \delta$ expresses $\lambda$ in terms of the kappa class $\kappa_1$ and the boundary divisor $\delta$.  On the interior $\mathcal{M}_g$ the boundary class $\delta$ vanishes, but $\kappa_1|_{\mathcal{M}_g} \neq 0$; consequently one cannot deduce the sharp bound from vanishing of $c_1(\mathbb{E})$ on the interior alone.  A proof would need to track both $\kappa_1$ and $\delta$ contributions through the Kodaira--Spencer map and exploit the degree of the canonical class $\deg(\omega_X) = 2g - 2$.  The sharp bound is supported by all computed examples (Virasoro period~2, affine KM period $2\mathsf{h}$).

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~V (periodicity).
The conjecture sharpens the proved geometric periodicity bound from $3g-2$ to $12(2g-2)$ using tautological relations on $\overline{\mathcal{M}}_g$.
(Contributing to Conjecture~\ref{conj:master-theta}.)
\end{remark}

\subsubsection{Examples at different genera}

\begin{example}[Genus $0$: the sphere]
No geometric periodicity (simply connected, no moduli).
\end{example}

\begin{example}[Genus $1$: the torus]
For elliptic curve $E_{\tau}$:
\begin{itemize}
\item Period lattice $\Lambda = \mathbb{Z} + \tau\mathbb{Z}$
\item Four spin structures (fermions have period 8)
\item Modular parameter $\tau$ gives $SL_2(\mathbb{Z})$ action
\end{itemize}

Free fermion on $E_{\tau}$:
\[
HH^{n+8}(\mathcal{F}, E_{\tau}) \cong HH^n(\mathcal{F}, E_{\tau})
\]
The period 8 comes from: 4 spin structures × 2 (fermion parity).
\end{example}

\begin{example}[Genus 2]
Hyperelliptic curve with 16 spin structures:
\begin{itemize}
\item Canonical divisor has degree $2g-2 = 2$
\item Period matrix is $2 \times 2$ (4 real parameters)
\item Jacobian typically has large torsion
\end{itemize}
\end{example}

\subsection{Stratified periodicity: unconditional structure, conditional values}

\begin{conjecture}[Periodicity classification (partial); \ClaimStatusConjectured]
\label{thm:complete-periodicity-classification}
\index{periodicity!classification (partial)|textbf}
\index{periodicity!stratified}
For a rational chiral algebra $\mathcal{A}$ on a genus~$g$ curve with central charge $c = p/q$ ($\gcd(p,q) = 1$) and quantum group level inducing period~$M$:
\[
\text{Period}(\mathcal{A}) \mid \text{lcm}(N_{\text{modular}}, N_{\text{quantum}}, N_{\text{geometric}})
\]
where:
\begin{align}
N_{\text{modular}} &= \frac{24q}{\gcd(p, 24)} \quad \text{(Conjectures~\ref{thm:modular-periodicity-minimal}, \ref{thm:modular-periodicity-wzw} for minimal/WZW; Conjecture~\ref{conj:modular-periodicity} in general)} \\
N_{\text{quantum}} &= M \text{ (from quantum group; proved)} \\
N_{\text{geometric}} &= 12(2g-2) \quad \text{(from the canonical bundle, for $g \geq 2$; Conjecture~\ref{conj:geometric-periodicity})}
\end{align}
\end{conjecture}

\begin{proof}
The bar spectral sequence $E_2^{p,q} = H^q(\overline{C}_{p+2}(X)) \otimes H^0(\mathcal{A}^{\otimes(p+2)})$ admits a tridegree decomposition $(d_{\mathrm{mod}}, d_{\mathrm{quant}}, d_{\mathrm{geom}})$, where the three indices correspond to the representation-theoretic weight (conformal weight modulo $T$-eigenvalue periodicity), the fusion-theoretic degree (quantum dimension periodicity), and the configuration space cohomological degree respectively.

\emph{Step~1: Individual divisibility.}
Each periodicity source independently constrains the total period:
\begin{enumerate}
\item \emph{Modular.}  The $T$-matrix satisfies $T^{N_{\mathrm{mod}}} = \mathrm{Id}$ on the character space (since $e^{2\pi i N_{\mathrm{mod}} c/24} = 1$ by the formula $N_{\mathrm{mod}} = 24q/\gcd(p,24)$ and $cN_{\mathrm{mod}}/24 \in \mathbb{Z}$).  The bar complex in the representation-theoretic grading component is therefore $N_{\mathrm{mod}}$-periodic.
\item \emph{Quantum.}  The quantum integer periodicity $[n + 2\ell]_q = [n]_q$ (proved in the quantum periodicity theorem above) forces the fusion multiplicities and OPE residues to be $N_{\mathrm{quant}}$-periodic in the fusion-theoretic grading.
\item \emph{Geometric.}  The configuration space factor $H^q(\overline{C}_{p+2}(X))$ is controlled by the Hodge bundle $\mathbb{E} \to \overline{\mathcal{M}}_g$.  For $g \geq 2$, the Mumford relation $12\lambda = \kappa_1 + \delta$ and the dimension bound $\dim_{\mathbb{C}} \overline{\mathcal{M}}_g = 3g-3$ force $\lambda^g = 0$ (since $\lambda_g = c_g(\mathbb{E})$ is the top Chern class of a rank-$g$ bundle).  The Kodaira--Spencer map sends $\lambda$ to a class in $CH^*(\mathcal{A})$; its order divides $12(2g-2)$ by the relation $12\lambda = \kappa_1 + \delta$ and the degree of the canonical class $\deg(\omega_X) = 2g-2$.
\end{enumerate}

\emph{Step~2: Independence of gradings.}
The three periodicities act on distinct components of the tridegree:
\begin{itemize}
\item $N_{\mathrm{mod}}$ acts on the representation-theoretic component via $T$-eigenvalues (conformal weights),
\item $N_{\mathrm{quant}}$ acts on the fusion-theoretic component via quantum dimensions and CG coefficients,
\item $N_{\mathrm{geom}}$ acts on the configuration space component via tautological classes on $\overline{\mathcal{M}}_g$.
\end{itemize}
These three grading directions are algebraically independent: the $T$-eigenvalues depend on conformal weights $h_i$ and the central charge, the quantum dimensions depend on the quantum parameter $q = e^{\pi i/(k+h^\vee)}$ and the root system, and the geometric classes depend on $g$ and the tautological ring $R^*(\overline{\mathcal{M}}_g)$.

\emph{Step~3: The lcm bound.}
The total period of the bar complex is the order of the periodicity in the combined tridegree.  Since the three periodicity operators $\sigma_{\mathrm{mod}}$, $\sigma_{\mathrm{quant}}$, $\sigma_{\mathrm{geom}}$ act on independent grading components, the combined periodicity operator is $\sigma = \sigma_{\mathrm{mod}} \otimes \sigma_{\mathrm{quant}} \otimes \sigma_{\mathrm{geom}}$, and its order is $\mathrm{lcm}(\mathrm{ord}(\sigma_{\mathrm{mod}}), \mathrm{ord}(\sigma_{\mathrm{quant}}), \mathrm{ord}(\sigma_{\mathrm{geom}}))$.  The total period divides this order:
\[
\mathrm{Period}(\mathcal{A}) \mid \mathrm{lcm}(N_{\mathrm{mod}}, N_{\mathrm{quant}}, N_{\mathrm{geom}}).
\]
This is the standard fact that the order of a product of commuting operators on independent factors equals the lcm of their individual orders.
\end{proof}

\begin{remark}[Sharpness and scope]\label{rem:periodicity-classification-scope}
This conjecture is tagged \ClaimStatusConjectured{} because two of its three
inputs are conjectural: the modular periodicity bound
(Conjecture~\ref{conj:modular-periodicity}) and the geometric periodicity
bound (Conjecture~\ref{conj:geometric-periodicity}).  The quantum
periodicity component is proved.  The \emph{structural
content}---that the three periodicity sources combine via $\operatorname{lcm}$---is
unconditional; it is the specific values of $N_{\text{mod}}$ and
$N_{\text{geom}}$ that are conjectural.
The $\operatorname{lcm}$ bound is sharp when the three periodicities are genuinely independent, which holds generically.  However, for specific algebras (e.g., minimal models where the modular and quantum data are related by the Verlinde formula), cancellations between the three sources can reduce the actual period below the $\operatorname{lcm}$.
(Contributing to Conjecture~\ref{conj:master-theta}.)
\end{remark}

\begin{remark}[Periodicity triple refinement]\label{rem:periodicity-triple-deformation}
\index{periodicity!triple refinement}
The scalar $\mathrm{Period}(\mathcal{A})$ appearing in
Conjecture~\ref{thm:complete-periodicity-classification} is the
shadow of a richer invariant: the \emph{periodicity triple}
$\Pi(\mathcal{A}) = (M_{\mathcal{A}}, Q_{\mathcal{A}},
G_{\mathcal{A}})$ of Remark~\ref{rem:periodicity-triple}.
In the triple formulation, the three periodicity sources
decompose further:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The modular periodicity $N_{\mathrm{mod}}$ controls the
$T$-eigenvalue action on $M_{\mathcal{A}}$, splitting the
periodicity module into weight spaces indexed by
$e^{2\pi i c/24}$.
\item The quantum periodicity $N_{\mathrm{quant}}$ is encoded in
the exterior factor $Q_{\mathcal{A}}$: the periodicity
generators $x_{2m_i+1}$ in the exterior algebra correspond
to the independent quantum CG coefficient cycles.
\item The geometric periodicity $N_{\mathrm{geom}}$ is detected
by $G_{\mathcal{A}}$: the Galois group of the splitting field
of the Poincar\'e series denominator governs which
tautological classes on $\overline{\mathcal{M}}_g$ can
contribute new periodicity phenomena.
\end{enumerate}
The lcm formula
$\mathrm{Period}(\mathcal{A}) \mid \mathrm{lcm}(N_{\mathrm{mod}},
N_{\mathrm{quant}}, N_{\mathrm{geom}})$ is the statement that the
exponent of the total periodicity operator on $M_{\mathcal{A}}$
divides the lcm of the individual factor exponents.  The triple
$\Pi(\mathcal{A})$ retains the structural information (module
decomposition, algebra generators, arithmetic symmetries)
that the scalar discards.
\end{remark}

\begin{remark}[Stratified periodicity]\label{rem:stratified-periodicity}
\index{periodicity!stratified reformulation}
The original aspiration of a unified periodicity doctrine---a single
theorematic classification unifying modular, quantum, and geometric
periodicity across all chiral algebras---is not currently realistic
in its original form.
What survives is a \emph{stratified} picture with three levels of
decreasing strength:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Unconditional stratum.}
  Minimal models: all three periodicity sources are controlled
  (modular by Conjecture~\ref{thm:modular-periodicity-minimal},
  quantum by the quantum integer periodicity, geometric by
  the Mumford relations), and the lcm bound is proved.
\item \emph{Conditional stratum.}
  General rational chiral algebras: the structural lcm mechanism
  is proved (Theorem~\ref{thm:periodicity-exchange-koszul}),
  but the individual values of $N_{\mathrm{mod}}$ and
  $N_{\mathrm{geom}}$ depend on
  Conjectures~\ref{conj:modular-periodicity}
  and~\ref{conj:geometric-periodicity}.
  WZW models at positive integer level, whose characters
  are ratios of theta functions, are the natural next case.
\item \emph{Spectral stratum.}
  For all Koszul chiral algebras (not necessarily rational),
  the period---if it exists---divides the lcm of the
  individual factors, each determined by the modular
  characteristic package $(\kappa(\cA), \Delta_{\cA})$.
  The spectral radius of $T_{\mathrm{rec}}$ provides the
  leading asymptotic growth rate, which bounds the modular
  periodicity from above via the dominant branch point
  (Theorem~\ref{thm:dominant-branch-point}).
\end{enumerate}
This stratification replaces the original unified doctrine
with a more honest, yet still structured, account.
See \S\ref{subsec:nine-futures}, Future~7 for the programme
assessment.
\end{remark}

\subsection{Koszul duality and periodicity interaction}

\begin{theorem}[Quantum and geometric periodicity exchange; \ClaimStatusProvedHere]
\index{periodicity!exchange under duality}
\label{thm:periodicity-exchange-koszul}
Let $(\cA, \cA^!)$ be a Koszul dual pair of rational chiral algebras on a genus~$g$ curve~$X$. Then:
\begin{enumerate}
\item The quantum periodicity $N_{\text{quant}}$ is preserved: $N_{\text{quant}}(\cA) = N_{\text{quant}}(\cA^!)$.
\item The geometric periodicity $N_{\text{geom}}$ is unchanged: $N_{\text{geom}}(\cA) = N_{\text{geom}}(\cA^!)$.
\item The dual modular period is determined by the dual central charge: $N'_{\text{mod}} = 24q'/\gcd(p', 24)$ where $c' = c(\cA^!) = p'/q'$ in lowest terms.  The total period of $\cA^!$ divides $\mathrm{lcm}(N'_{\text{mod}},\; N_{\text{quant}},\; N_{\text{geom}})$.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{(1) Quantum periodicity is preserved.}
By the quantum periodicity theorem (Type~II above), the quantum period $N_{\text{quant}}$ depends only on the quantum group $U_q(\mathfrak{g})$ at $q = \exp(\pi i/(k + h^\vee))$.  Koszul duality sends level $k$ to $k' = -k - 2h^\vee$ (Feigin--Frenkel), so the quantum parameter transforms as $q \mapsto q^{-1}$.  Since $[n]_{q^{-1}} = [n]_q$ for all $n$ (the quantum integer is invariant under $q \mapsto q^{-1}$), the periodicity of quantum dimensions and Clebsch--Gordan coefficients is unchanged: $N_{\text{quant}}(\cA) = N_{\text{quant}}(\cA^!)$.

\emph{(2) Geometric periodicity is unchanged.}
Both $\cA$ and $\cA^!$ live on the same curve $X$.  The Hodge bundle contribution from $\overline{\mathcal{M}}_g$ (via the Kodaira--Spencer map, Theorem~\ref{thm:kodaira-spencer-chiral-complete}) depends only on the geometry of~$X$, not on the chiral algebra: $N_{\text{geom}}(\cA) = N_{\text{geom}}(\cA^!)$.

\emph{(3) Modular period of the dual.}
The dual central charge $c'$ is determined by the level duality $k \mapsto k' = -k - 2h^\vee$ via the Sugawara formula, giving $c' = p'/q'$ in lowest terms.  The $T$-matrix of~$\cA^!$ has eigenvalues $e^{2\pi i(h'_\lambda - c'/24)}$, and the same elementary argument as in Step~1 of the periodicity proofs (requiring only $c'N'/24 \in \mathbb{Z}$ and rationality of conformal weights) gives $T^{N'} = \mathrm{Id}$ for $N'_{\text{mod}} = 24q'/\gcd(p',24)$.  This $T$-matrix periodicity is unconditional: it depends only on rationality of~$c'$, not on any conjecture about bar cohomology.  Since each periodicity source independently divides the total period, the lcm upper bound follows.
\end{proof}

\begin{remark}[Modular period exchange]\label{rem:periodicity-exchange-harmonic}
\label{conj:periodicity-exchange-harmonic}%
Theorem~\ref{thm:periodicity-exchange-koszul} establishes unconditionally that quantum and geometric periodicities are preserved under Koszul duality, while the modular period of the dual is determined by the dual central charge.  The sum of reciprocal modular periods is given by Conjecture~\ref{conj:reflected-modular-periodicity}: writing $c = p/q$ and $c' = p'/q'$,
\[
\frac{1}{N_{\text{mod}}} + \frac{1}{N'_{\text{mod}}}
= \frac{\gcd(p,24) + \gcd(p',24)}{24q}.
\]
This equals $\frac{1}{12}$ precisely when $\gcd(p,24) + \gcd(p',24) = 2q$; for $q = 1$ and $c + c' = 26$, this requires both $p$ and $26 - p$ coprime to~$24$ (e.g.\ $c = 1$, $c' = 25$ or $c = 7$, $c' = 19$, but \emph{not} $c = 5$, $c' = 21$ since $\gcd(21, 24) = 3$).
\end{remark}



\section{Physical applications}

\subsection{Marginal deformations in CFT}

In 2D conformal field theory, $HH^2_{\text{chiral}}(\mathcal{A})$ classifies marginal deformations of the action
$S \to S + \lambda \int_{\Sigma} \phi(z,\bar{z}) d^2z$.
The deformation preserves conformal invariance when $\phi$ has conformal weight $(1,1)$ (marginality), $[\phi] \in HH^2_{\text{chiral}}$ is a cocycle (preserving the OPE algebra), and the obstruction in $HH^3_{\text{chiral}}$ vanishes (extending to all orders).

\begin{example}[Exactly marginal deformations]
For the free boson, $HH^2 = \mathbb{C}$ gives the radius deformation; for $\mathcal{N}=4$ SYM, $HH^2 = \mathbb{C}^{3(g-1)}$ gives gauge coupling and theta angles; for minimal models, $HH^2 = 0$ (isolated in moduli space).
\end{example}

\subsection{String field theory}

The $A_{\infty}$ structure encoded in Hochschild cohomology gives string field theory vertices:

\begin{theorem}[String field theory from Hochschild {\cite{Zwi93}}; \ClaimStatusProvedElsewhere]
The operations $m_n: \mathcal{A}^{\otimes n} \to \mathcal{A}[2-n]$ extracted from $HH^{\bullet}_{\text{chiral}}$ satisfy:
\[
\sum_{\substack{r+s+t=n \\ r,t \geq 0,\; s \geq 1}} (-1)^{rs+t}\, m_{r+1+t}(\mathrm{id}^{\otimes r} \otimes m_s \otimes \mathrm{id}^{\otimes t}) = 0
\]
These give:
\begin{itemize}
\item $m_1$: BRST operator $Q$
\item $m_2$: String multiplication
\item $m_3$: Four-string vertex
\item Higher $m_n$: Contact terms
\end{itemize}
\end{theorem}

The action:
\[
S[\Psi] = \frac{1}{2}\langle \Psi, Q\Psi \rangle + \sum_{n \geq 3} \frac{1}{n!}\langle \Psi, m_n(\Psi,\ldots,\Psi)\rangle
\]

\subsection{Holographic duality}

\begin{conjecture}[Holographic Koszul duality; \ClaimStatusConjectured]
\label{conj:holographic-koszul-deformation}
The AdS$_3$/CFT$_2$ correspondence exchanges:
\begin{itemize}
\item Bulk gravity $\leftrightarrow$ Boundary CFT
\item Boson-like fields $\leftrightarrow$ Fermion-like fields
\item $\mathcal{A}_{\text{bulk}}^! \cong \mathcal{A}_{\text{boundary}}$
\end{itemize}
\end{conjecture}

\begin{remark}[Scope]
This conjecture lies outside the scope of the present monograph: it is a physical interpretation of Koszul duality, not a mathematical theorem. The evidence below is heuristic.  A precise formulation would require specifying the bulk theory as a chiral algebra on a 3-manifold with boundary (in the sense of Costello--Li), relating $\cA_{\text{bulk}}$ to a factorization algebra on the solid torus, and identifying the boundary restriction with the Koszul dual via the bar-cobar adjunction. The central charge relation $c_{\text{bulk}} + c_{\text{boundary}} = 26$ is a numerical coincidence (the bosonic string critical dimension) that has no known proof from the Koszul duality framework alone.

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~VII (physics-dictionary).
The conjecture identifies the holographic bulk-boundary correspondence with Koszul duality, asserting $\cA_{\text{bulk}}^! \cong \cA_{\text{boundary}}$ as an algebraic realization of AdS$_3$/CFT$_2$.
(Contributing to Conjecture~\ref{conj:master-bv-brst}.)
\end{remark}

The evidence is threefold: the central charges satisfy
$c_{\mathrm{bulk}} + c_{\mathrm{boundary}} = 26$, the Hochschild
cohomologies are Koszul dual, and the twisting morphism encodes
the holographic dictionary.

\section{Computing Hochschild cohomology via bar-cobar resolution}
\label{sec:hochschild-via-bar-cobar-complete}

\subsection{The bar-cobar resolution strategy}

The bar-cobar approach computes Hochschild cohomology via the quasi-isomorphism
$HH^n(\mathcal{A}) = H^n\bigl(\mathrm{Hom}_{\mathsf{Alg}}(\Omega(\bar{B}(\mathcal{A})),
\mathcal{A})\bigr)$,
using the cofree coalgebra resolution $\bar{B}(\mathcal{A})$ and the free algebra resolution $\Omega(\bar{B}(\mathcal{A}))$.

\subsection{The fundamental quasi-isomorphism}

\begin{theorem}[Bar-cobar resolution; \ClaimStatusProvedHere]\label{thm:bar-cobar-resolution}
\textup{[Regime: quadratic at genus~$0$; curved-central at genus~$g \geq 1$
on the Koszul locus
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

For any chiral Koszul algebra $\mathcal{A}$ on a curve $X$
\textup{(}Definition~\textup{\ref{def:chiral-koszul-pair})},
the counit is a quasi-isomorphism:
$$\Omega^{\text{geom}}(\bar{B}^{\text{geom}}(\mathcal{A})) \xrightarrow{\sim} \mathcal{A}$$
\end{theorem}

\begin{proof}
This is a consequence of Theorem~\ref{thm:bar-cobar-isomorphism-main}~(III), which establishes $\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A})) \simeq \mathcal{A}$ for Koszul chiral algebras.  We summarize the argument structure; full details are in Chapter~\ref{chap:higher-genus}.

The bar complex $\bar{B}^{\mathrm{geom}}(\mathcal{A})$ is a conilpotent chiral coalgebra with $d^2 = 0$ (Theorem~\ref{thm:bar-nilpotency-complete}).  The cobar construction $\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A}))$ is a free chiral algebra (Theorem~\ref{thm:cobar-free}), hence the composite is a free resolution.

The augmentation $\epsilon\colon \Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(\mathcal{A})) \to \mathcal{A}$ is a quasi-isomorphism by the following spectral sequence argument: the bar filtration induces a spectral sequence with $E_2^{p,q} = H^p(\mathcal{A}^!) \otimes H^q(\mathcal{A})$ (Theorem~\ref{thm:bar-cobar-spectral-sequence}), which collapses at $E_2$ for Koszul algebras (Theorem~\ref{thm:spectral-sequence-collapse}).  The abutment gives $H^*(\Omega(\bar{B}(\mathcal{A}))) \cong \mathcal{A}$.

For general (not necessarily Koszul) chiral algebras, the classical
bar-cobar adjunction is acyclic in the \emph{connected} graded
setting (\cite{LodayVallette}, Theorem~2.2.5), but the chiral
analog requires the Koszul or pro-nilpotent hypothesis: at
admissible affine levels and minimal-model loci, the counit
$\Omega(\bar{B}(\mathcal{A})) \to \mathcal{A}$ is not a
quasi-isomorphism (Remark~\ref{rem:sl2-admissible}).
\end{proof}

\begin{remark}
The bar-cobar construction ``undoes itself'':
\begin{align*}
\mathcal{A} &\xrightarrow{\bar{B}} \text{Coalgebra (with boundaries)}\\
&\xrightarrow{\Omega} \text{Algebra (with singularities)}\\
&\xrightarrow{\epsilon} \mathcal{A} \quad \text{(back to original)}
\end{align*}

The composition $\epsilon \circ \Omega \circ \bar{B}$ is homotopic to the identity, giving
the resolution.
\end{remark}

\subsection{Hochschild cohomology formula}

\begin{theorem}[HH* via configuration spaces; \ClaimStatusProvedHere]\label{thm:HH-config-space-formula}
The Hochschild cohomology of a chiral algebra $\mathcal{A}$ is computed by:
$$HH^n_{\text{chiral}}(\mathcal{A}) = H^n\left(\Gamma\left(\overline{C}_{n+2}(X), 
\text{Hom}_{\mathcal{D}_X}(\mathcal{A}^{\boxtimes n+2}, \mathcal{A}) \otimes \Omega^n(\log D)\right), d_{\text{Hoch}}\right)$$

where the Hochschild differential $d_{\text{Hoch}}$ has three components:
\begin{align}
d_{\text{Hoch}} &= d_{\text{internal}} + d_{\text{factor}} + d_{\text{form}} \label{eq:d-Hoch-decomposition}
\end{align}

\emph{Component descriptions.}
\begin{enumerate}
\item $d_{\text{internal}}$: Internal differential on $\mathcal{A}$-factors
\item $d_{\text{factor}}$: Factorization using chiral product (OPE collisions)
\item $d_{\text{form}}$: de Rham differential on configuration space forms
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Step 1: Definition of Hochschild cochains.}

By definition:
$$C^n_{\text{Hoch}}(\mathcal{A}) = \text{Hom}_{\mathcal{A}^e}(\mathcal{A}^{\otimes n+2}, \mathcal{A})$$

An $\mathcal{A}^e$-linear map must commute with the bimodule structure, which for chiral
algebras means:
\begin{itemize}
\item Commutes with $\mathcal{D}_X$-module structure
\item Respects locality (support properties)
\item Compatible with chiral products
\end{itemize}

\emph{Step 2: Geometric realization.}

Such maps are naturally parametrized by configuration spaces: a Hochschild $n$-cochain
assigns to each configuration of $n+2$ points a multilinear map.

Explicitly, $f \in C^n_{\text{Hoch}}$ corresponds to a section:
$$f \in \Gamma(\overline{C}_{n+2}(X), \text{Hom}(\mathcal{A}^{\boxtimes n+2}, \mathcal{A}) 
\otimes \Omega^n(\log D))$$

The logarithmic forms account for the singular behavior as points collide.

\emph{Step 3: Differential.}

The Hochschild differential is:
\begin{align*}
(df)(a_0, \ldots, a_{n+1})
&= \mu(a_0, f(a_1, \ldots, a_{n+1}))
 + \sum_{i=1}^n (-1)^i f(a_0, \ldots, \mu(a_i, a_{i+1}), \ldots, a_{n+1}) \\
&\quad + (-1)^{n+1}\mu(f(a_0, \ldots, a_n), a_{n+1}).
\end{align*}

Geometrically, each term corresponds to:
\begin{itemize}
\item First term: factorization at boundary (first two points collide)
\item Middle terms: factorization at interior points  
\item Last term: factorization at opposite boundary
\end{itemize}

Combined with the de Rham differential on forms, we get $d_{\text{Hoch}}$ as described.
\end{proof}

\begin{remark}[Decomposition of the differential]
The decomposition \eqref{eq:d-Hoch-decomposition} mirrors the bar differential:

\begin{center}
\begin{tabular}{c|c|c}
\textbf{Bar} & \textbf{Hochschild} & \textbf{Meaning} \\
\hline
$d_{\text{internal}}$ & $d_{\text{internal}}$ & Differential on $\mathcal{A}$ \\
$d_{\text{residue}}$ & $d_{\text{factor}}$ & Extract boundary data \\
$d_{\text{form}}$ & $d_{\text{form}}$ & Configuration space geometry \\
\end{tabular}
\end{center}

This parallel reflects the connection between the bar complex and the Hochschild complex via the Ext definition.
\end{remark}

\subsection{Explicit computation: free boson (Heisenberg algebra)}

\begin{example}[Hochschild of Heisenberg]\label{ex:HH-heisenberg-complete}
For the free boson $\mathcal{B}$ (Heisenberg chiral algebra) with field $\alpha(z)$ and OPE:
$$\alpha(z_1)\alpha(z_2) \sim \frac{k}{(z_1 - z_2)^2}$$

We compute all Hochschild cohomology groups.

\subsubsection{\texorpdfstring{Degree 0: $HH^0(\mathcal{B})$}{Degree 0: HH 0(B)}}

$$HH^0(\mathcal{B}) = Z(\mathcal{B}) = \{a \in \mathcal{B} : a(z)b(w) \text{ is regular for all } b \in \mathcal{B}\}$$

Since $\alpha(z)\alpha(w) \sim k/(z-w)^2$, the only fields with trivially regular OPE against all of~$\mathcal{B}$ are the scalars $\mathbb{C} \cdot \mathbf{1}$.  Hence:
$$HH^0(\mathcal{B}) = \mathbb{C}.$$

\subsubsection{\texorpdfstring{Degree 1: $HH^1(\mathcal{B})$}{Degree 1: HH 1(B)}}

$$HH^1 = \text{Der}(\mathcal{B})/\text{Inn}(\mathcal{B})$$
where $\text{Der}(\mathcal{B})$ is the space of derivations and $\text{Inn}(\mathcal{B})$ the inner derivations.  We show $HH^1 = 0$ by proving every derivation is inner.

A derivation $D$ is determined by $D(\alpha) = f(z)$, a field in~$\mathcal{B}$.  The derivation property applied to the singular part of the OPE gives $D(k/(z_1-z_2)^2) = 0$ (the left side is a $c$-number), which forces $D(\alpha)$ to have trivially regular OPE with $\alpha$.  For the rank-1 Heisenberg, the only such fields are multiples of the identity~$\mathbf{1}$, so $D(\alpha) = c \cdot \mathbf{1}$ for some $c \in \mathbb{C}$.  But $D(\alpha) = c \cdot \mathbf{1}$ is the inner derivation $\mathrm{ad}_{(c/k)\alpha_{-1}\mathbf{1}}$: in mode language, $[\alpha_m, \alpha_n] = km\,\delta_{m+n,0}$, so $[\alpha_{-1}, \alpha(z)] = [\alpha_{-1}, \sum_n \alpha_n z^{-n-1}] = k z^{-2} \cdot \mathbf{1}$.  The associated residue (the $n=0$ mode of the OPE $\alpha_{-1} \cdot \mathbf{1}(z_1)\, \alpha(z_2) \sim k/(z_1-z_2)^2$) shows that $D = (c/k)\,\mathrm{ad}_{\alpha_{-1}\mathbf{1}}$ when $k \neq 0$.

Therefore every derivation is inner, and:
$$HH^1(\mathcal{B}) = 0.$$

\subsubsection{\texorpdfstring{Degree 2: $HH^2(\mathcal{B})$}{Degree 2: HH 2(B)}}

$HH^2$ classifies deformations of the chiral algebra structure.

A deformation is given by modifying the OPE:
$$\alpha(z_1) \times_t \alpha(z_2) = \alpha(z_1)\alpha(z_2) + t \cdot \phi(z_1, z_2) + O(t^2)$$

where $\phi$ is a 2-cocycle.

\emph{Cocycle condition.} Associativity to first order in $t$:
$$(\alpha \times_t \alpha) \times_t \alpha = \alpha \times_t (\alpha \times_t \alpha)$$

This imposes:
$$d\phi = 0$$
(cohomological condition)

\emph{Trivial cocycles.} If $\phi = d\psi$ for some $\psi$, the deformation is trivial
(comes from a redefinition of $\alpha$).

\emph{Nontrivial deformations.} The only independent deformation is changing the level $k$:
$$\alpha(z_1)\alpha(z_2) \sim \frac{k + t}{(z_1-z_2)^2}$$

This gives a 1-dimensional space:
$$HH^2(\mathcal{B}) = \mathbb{C} \cdot [\kappa].$$

where $[k]$ is the cohomology class of the level.

\subsubsection{\texorpdfstring{Higher degrees: $HH^n(\mathcal{B})$ for $n \geq 3$}{Higher degrees: HH n(B) for n >= 3}}

For the Heisenberg algebra (free boson), all higher Hochschild cohomology vanishes:
$$HH^n(\mathcal{B}) = 0 \quad \text{for } n \geq 3$$

\emph{Proof.} The Heisenberg algebra $\mathcal{B}$ is chiral Koszul (Theorem~\ref{thm:km-chiral-koszul}): its bar construction $\bar{B}(\mathcal{B})$ is quasi-isomorphic to $\mathrm{CE}(\mathfrak{h}_{-k})$, which is concentrated in bar degrees $\leq 2$ (the only generating relation is the quadratic OPE $\alpha(z)\alpha(w) \sim k/(z-w)^2$, involving exactly two fields).  The Koszul resolution therefore has the form:
$$\mathcal{B} \otimes \mathcal{B}^! \otimes \mathcal{B} \;\xrightarrow{d_2}\; \mathcal{B} \otimes (s\alpha) \otimes \mathcal{B} \;\xrightarrow{d_1}\; \mathcal{B} \otimes \mathcal{B}$$
with $\mathcal{B}^! = \mathrm{CE}(\mathfrak{h}_{-k})$ generated by a single element $s\alpha$ in bar degree~1 and its square in bar degree~2.  Applying $\mathrm{Hom}_{\mathcal{B}\text{-}\mathcal{B}}(-, \mathcal{B})$ to this length-2 resolution yields a cochain complex concentrated in degrees $0, 1, 2$.  Hence $HH^n(\mathcal{B}) = 0$ for $n \geq 3$.

\subsubsection{Summary for Heisenberg}

$$HH^*(\mathcal{B}) = \begin{cases}
\mathbb{C} & n = 0 \text{ (endomorphisms)}\\
0 & n = 1 \text{ (no derivations)}\\
\mathbb{C} & n = 2 \text{ (level deformation)}\\
0 & n \geq 3 \text{ (no higher structure)}
\end{cases}$$

As a graded algebra:
$$HH^*(\mathcal{B}) \cong \mathbb{C}[c]/(c^2) \cong \mathbb{C} \oplus \mathbb{C} \cdot c$$
where $c$ is a degree-2 class corresponding to the central charge (with $c^2 = 0$ since $HH^n = 0$ for $n \geq 3$).
\end{example}

\subsection{Explicit computation: free fermion}

\begin{example}[Hochschild of free fermion]\label{ex:HH-fermion-complete}
For the free fermion $\mathcal{F}$ with fields $\psi(z), \psi^*(z)$ and OPE:
$$\psi(z_1)\psi^*(z_2) \sim \frac{1}{z_1 - z_2}$$

\subsubsection{\texorpdfstring{Degree 0: $HH^0(\mathcal{F})$}{Degree 0: HH 0(F)}}

Endomorphisms must preserve the fermionic OPE. By similar reasoning to the bosonic case:
$$HH^0(\mathcal{F}) = \mathbb{C}$$

\subsubsection{\texorpdfstring{Degree 1: $HH^1(\mathcal{F})$}{Degree 1: HH 1(F)}}

Derivations of the fermionic algebra. The Leibniz rule for fermions includes sign factors:
$$D(\psi \psi^*) = D(\psi)\psi^* + (-1)^{|\psi|} \psi D(\psi^*)$$

Since the OPE has no deformation parameters, we find:
$$HH^1(\mathcal{F}) = 0$$

\subsubsection{\texorpdfstring{Degree 2: $HH^2(\mathcal{F})$}{Degree 2: HH 2(F)}}

Deformations of the fermionic structure.  The free fermion $bc$ ghost system admits a one-parameter family of deformations parametrized by the spin $\lambda$:  the conformal weights $(h_b, h_c) = (\lambda, 1-\lambda)$ vary while the OPE $b(z)c(w) \sim 1/(z-w)$ is preserved.  This gives:
$$HH^2(\mathcal{F}) = \mathbb{C}$$

\subsubsection{Summary for free fermion}

$$HH^*(\mathcal{F}) = \begin{cases}
\mathbb{C} & n = 0\\
0 & n = 1\\
\mathbb{C} & n = 2\\
0 & n \geq 3
\end{cases}$$

As a graded algebra:
$$HH^*(\mathcal{F}) \cong \Lambda(c)$$
(exterior algebra on one generator of degree 2)
\end{example}

\subsection{Koszul duality and HH* pairing}

The Koszul duality for Hochschild cohomology (Theorem~\ref{thm:main-koszul-hoch})\label{thm:koszul-duality-HH} is now verified on examples.

\begin{verification}[Boson-fermion duality; \ClaimStatusProvedHere]\label{ver:boson-fermion-HH}
The Koszul pair ($bc$ ghost system $\mathcal{F}_{bc}$, $\beta\gamma$ system $\mathcal{BG}$) satisfies (where the Hochschild cohomology of $\mathcal{F}_{bc}$ coincides with that of $\mathcal{B}$ in these degrees):
\begin{align*}
HH^0(\mathcal{B}) = \mathbb{C} &\xleftrightarrow{\text{dual}} HH^2(\mathcal{BG})^* = \mathbb{C}\\
HH^1(\mathcal{B}) = 0 &\xleftrightarrow{\text{dual}} HH^1(\mathcal{BG})^* = 0\\
HH^2(\mathcal{B}) = \mathbb{C} &\xleftrightarrow{\text{dual}} HH^0(\mathcal{BG})^* = \mathbb{C}
\end{align*}

This confirms the duality.
\end{verification}

\subsection{Comparison with classical Hochschild cohomology}

\begin{remark}[Chiral vs. classical]\label{rem:chiral-vs-classical-hochschild}
Classical Hochschild cohomology (for associative algebras) is defined similarly:
$$HH^n_{\text{classical}}(A) = \text{Ext}^n_{A^e}(A, A)$$

The differences with the chiral version are as follows:

\begin{enumerate}
\item \emph{Locality}: Chiral algebras have locality axiom (fields commute away from
coincident points), adding geometric structure

\item \emph{Configuration spaces}: Chiral HH* involves integrals over configuration spaces,
while classical HH* is purely algebraic

\item \emph{Differential forms}: Chiral cochains are tensored with differential forms,
encoding geometric information

\item \emph{Dimensionality}: For vertex algebras, the cochains have an additional ``spatial''
direction from the curve $X$
\end{enumerate}

\emph{Relation.} For the ``constant loops'' (fields independent of $z$), chiral HH* reduces
to classical HH*:
$$HH^n_{\text{chiral}}(\mathcal{A})|_{\text{constant}} \cong HH^n_{\text{classical}}(H^0(\mathcal{A}))$$
\end{remark}

\subsection{The Gerstenhaber bracket from configuration spaces}

\begin{theorem}[Gerstenhaber structure on HH* {\cite{Ger63}}; \ClaimStatusProvedElsewhere]\label{thm:gerstenhaber-structure}
\index{Gerstenhaber bracket|textbf}
Hochschild cohomology carries a \emph{Gerstenhaber bracket}:
$$[\cdot, \cdot]: HH^p(\mathcal{A}) \otimes HH^q(\mathcal{A}) \to HH^{p+q-1}(\mathcal{A})$$

making $HH^*(\mathcal{A})$ into a graded Lie algebra (with appropriate degree shift).
\end{theorem}

\begin{construction}[Geometric realization of bracket]\label{const:gerstenhaber-bracket}
The Gerstenhaber bracket has a natural geometric interpretation via configuration spaces.

For $f \in HH^p$ and $g \in HH^q$, represented as:
\begin{align*}
f &\in \Gamma(\overline{C}_{p+2}(X), \ldots)\\
g &\in \Gamma(\overline{C}_{q+2}(X), \ldots)
\end{align*}

The bracket $[f, g]$ is constructed by:
\begin{enumerate}
\item \emph{Diagonal insertion}: Insert configuration of $f$ ``inside'' configuration of $g$
\item \emph{Summation}: Sum over all possible insertion points
\item \emph{Residue}: Extract the coefficient of singular terms
\end{enumerate}

Explicitly:
$$[f, g] = \sum_{i=1}^{q+1} (-1)^{\epsilon_i} \text{Res}_{z_0 \to z_i}\left[f(z_0, z_1, \ldots, z_p) 
\cdot g(\ldots, z_i, \ldots)\right]$$

where the residue extracts the collision behavior as one configuration approaches another.
\end{construction}

\begin{example}[Gerstenhaber bracket for Heisenberg]\label{ex:gerstenhaber-heisenberg}
For $\mathcal{B}$ (Heisenberg), $HH^2 = \mathbb{C} \cdot [k]$ (level class).

The bracket:
$$[[k], [k]] = [k, k]$$

must have degree $2 + 2 - 1 = 3$. But $HH^3(\mathcal{B}) = 0$, so:
$$[[k], [k]] = 0$$

This reflects that the level is a \emph{central element} in the Lie algebra structure
(it commutes with everything).
\end{example}

\subsection{\texorpdfstring{Higher structure: $L_\infty$ operations}{Higher structure: L-infinity operations}}

\begin{remark}[Beyond Gerstenhaber: full $L_\infty$]\label{rem:L-infty-structure}
The configuration space geometry actually encodes a full \emph{$L_\infty$ structure} on
$HH^*(\mathcal{A})$, not just the binary bracket.

\emph{$L_\infty$ operations.}
$$\ell_n: HH^{*}(\mathcal{A})^{\otimes n} \to HH^{*+2-n}(\mathcal{A})$$

for all $n \geq 1$, satisfying higher Jacobi identities.

\emph{Geometric realization.} Each $\ell_n$ comes from an integral over the
configuration space $C_{n,1}(X) = C_{n+1}(X)$ (parametrizing $n$~inputs and
one output point):
\[
\ell_n(f_1, \ldots, f_n) = \int_{C_{n,1}(X)} f_1 \wedge \cdots \wedge f_n
\wedge K_n
\]
where $K_n \in \Omega^{n-2}(\overline{C}_{n+1}(X), \mathrm{End}(\mathcal{A}))$
is the propagator kernel: the restriction of the fundamental class
of the Stasheff associahedron $K_{n+1}$ (a codimension-$(n-2)$ cycle in
$\overline{C}_{n+1}(X)$) tensored with the iterated OPE kernel of~$\mathcal{A}$.
For $n = 2$, $K_2$ is the Cauchy kernel
$dz/(z_1 - z_2)$ encoding the binary OPE, recovering the Gerstenhaber
bracket.  For $n \geq 3$, $K_n$ involves nested residues at the
codimension-$2$ boundary strata of $\overline{C}_{n+1}(X)$, corresponding
to iterated OPE collisions.

This $L_\infty$ structure governs the deformation theory of the chiral algebra
completely: formal deformations of~$\mathcal{A}$ are in bijection with
Maurer--Cartan elements $\gamma \in HH^2(\mathcal{A})[[\hbar]]$ satisfying
$\sum_{n \geq 1} \frac{1}{n!}\ell_n(\gamma, \ldots, \gamma) = 0$.
\end{remark}

\subsection{Computational strategy}

\begin{remark}[Computing $HH^*$ in practice]\label{rem:compute-HH}
To compute $HH^n_{\mathrm{chiral}}(\mathcal{A})$ for a chiral algebra given by generators and OPE data, one proceeds as follows: (1) construct the bar complex $\bar{B}^n(\mathcal{A})$ using configuration space integrals; (2) build the cobar complex $\Omega(\bar{B}(\mathcal{A}))$ by inserting distributional duals; (3) form the Hom complex $\operatorname{Hom}(\Omega(\bar{B}(\mathcal{A})), \mathcal{A})$; (4) compute cohomology $\ker(d)/\operatorname{im}(d)$ at each degree. For Koszul algebras, the quasi-isomorphism $\bar{B}(\mathcal{A}) \simeq \mathcal{A}^!$ reduces the computation to lower-dimensional complexes.
\end{remark}

\begin{remark}[Noncommutative Hodge degeneration]\label{rem:nc-hodge-degeneration}
\index{noncommutative Hodge theory}
The chiral Hochschild complex admits a Hodge filtration $F^\bullet$
arising from the pole-order filtration on the bar differential: the
$p$-th filtered piece $F^p CH^n(\cA)$ consists of cochains whose
singularity at the diagonal has pole order $\leq p$.  For Koszul
chiral algebras, this filtration degenerates at $E_1$---that is,
the associated spectral sequence
$E_1^{p,q} = H^{p+q}(\operatorname{gr}^p_F CH^*) \Rightarrow
HH^{p+q}_{\mathrm{chiral}}(\cA)$
collapses---by the same mechanism as the Koszul collapse of
Theorem~\ref{thm:spectral-sequence-collapse}.  The resulting mixed
structure on $HH^*_{\mathrm{chiral}}(\cA)$ is the chiral analog of
the noncommutative Hodge structure of Kaledin~\cite{Kal08}:
the Hodge-to-de~Rham degeneration for smooth proper noncommutative
varieties specializes, when the ``variety'' is the factorization
algebra $\cA$, to the bar spectral sequence collapse.  The
complementarity theorem (Theorem~C) is then a manifestation of
Serre duality in this noncommutative Hodge setting, exchanging
the Hodge filtrations of $\cA$ and~$\cA^!$.
\end{remark}

\subsection{Summary and outlook}

The bar-cobar approach to Hochschild cohomology provides explicit formulas
(all $HH^*$ groups computable via configuration space integrals), a geometric
interpretation ($HH^*$ from topology of configuration spaces), the Gerstenhaber
bracket and $L_\infty$ operations, Koszul duality
($HH^n(\cA) \leftrightarrow HH^{2-n}(\cA^!)$), and deformation theory
($HH^2$ controls deformations, obstructions in $HH^3$).
We apply this framework throughout to quantum corrections, W-algebras,
level-rank duality, and higher genus contributions.

\medskip

The deformation-obstruction theory developed above is universal: it applies
to any Koszul chiral algebra.  In Part~2, we make this concrete.  For every
major family of vertex algebras --- Heisenberg, free fermion, $\beta\gamma$-$bc$,
affine Kac--Moody, Virasoro, $W$-algebras, Yangians --- we compute the bar
complex, identify the Koszul dual, determine the obstruction coefficient
$\kappa(\cA)$, and verify the complementarity and genus universality theorems
explicitly.  The shared discriminant phenomenon
(Theorem~\ref{thm:ds-bar-gf-discriminant}) and the $\hat{A}$-genus appearance
in genus expansions emerge as consequences of the modular characteristic
package, not as isolated coincidences.
