\subsection{Central finite-window curvature}

The finite-window topology separates three square tests.  A quadratic
finite-type algebra is controlled by the discrete conilpotent bar
coalgebra.  A curved algebra has a zero-ary term, and its raw unary
operator satisfies
\[
\mu_1^2=[\mu_0,-]_{\mu_2}.
\]
Central curvature kills this internal commutator, but it does not
erase the curvature from the bar construction.  An ordinary
square-zero bar differential appears only after a convergent
Maurer--Cartan twist with vanishing twisted curvature, or in the
period-corrected total model of
Theorem~\ref{thm:central-implies-strict}.  A genuinely filtered
algebra has non-descendant composites in arbitrarily high windows, so
the bar differential, cobar differential, and twisting cochain exist
only after finite-window completion.

\begin{proposition}[Central filtered deformations as curved models; \ClaimStatusProvedHere]\label{prop:filtered-to-curved-fc}
\index{filtered!vs curved}
\index{curved Ainfinity@curved $A_\infty$!filtered comparison}
Let $\mathcal{A}$ be an augmented chiral $A_\infty$ algebra with a
strong finite-window filtration in the sense of
Definition~\ref{idea:I-adic},
\[
\mathcal{A}=F^0\mathcal{A}\supset F^1\mathcal{A}=\bar{\mathcal{A}}
\supset F^2\mathcal{A}\supset\cdots,\qquad
\mathcal{A}\simeq\varprojlim_N\mathcal{A}_{\le N},\qquad
\mathcal{A}_{\le N}:=\mathcal{A}/F^{N+1}\mathcal{A},
\]
where every window $\mathcal{A}_{\le N}$ is finite-type and every
operation $\mu_r$ is continuous:
\[
\mu_r(F^{i_1}\mathcal{A},\ldots,F^{i_r}\mathcal{A})
\subset F^{i_1+\cdots+i_r}\mathcal{A}.
\]
Assume:
\begin{enumerate}
\item $\gr_F(\mathcal{A})$ is generated by its first non-zero
window with quadratic defining ideal $I_2$;
\item the deformation of the quadratic model is represented by a
compatible system of finite-window Maurer--Cartan elements, equivalently
by a continuous Maurer--Cartan element in the completed convolution
algebra
\[
\widehat{\operatorname{Conv}}
\bigl(\bar B(\gr_F\mathcal{A}),\gr_F\mathcal{A}\bigr);
\]
\item after choosing quadratic lifts, every non-quadratic relation
class is a quadratic consequence plus a correction in the closed ideal
generated by a single central zero-ary cycle
\[
\mu_0\in F^2 Z(\mathcal{A}),\qquad \mu_1(\mu_0)=0.
\]
\end{enumerate}
Then, after choosing topological generators $V$ lifting the first
non-zero window, $\mathcal{A}$ admits a completed curved $A_\infty$
model
\[
\mathcal{A}_{\mathrm{curv}}
=\widehat{T}_{\mathrm{ch}}(V)/\overline{(I_2)}
\]
carrying the completed $A_\infty$ operations induced by the
Maurer--Cartan element, with curvature $\mu_0$, together with a
continuous filtered morphism
\[
\mathcal{A}_{\mathrm{curv}}\longrightarrow\mathcal{A}
\]
whose finite-window cones are coacyclic in the completed coderived CDG
category.  If the finite windows are additionally equipped with one of
the square-zero total models of
Theorem~\ref{thm:central-implies-strict}, then the finite-window
truncations are quasi-isomorphisms of ordinary complexes; passing to
the completed limit is a quasi-isomorphism whenever the finite-stage
cone cohomology tower is Mittag--Leffler, in particular when those
cohomology groups are finite-dimensional.  If the centrality hypothesis
on $\mu_0$ is removed, the low identity is
$m_1^2=[\mu_0,-]_{\mu_2}$ and there is no ordinary raw-chain
quasi-isomorphism without an additional strictification.
\end{proposition}

\begin{proof}
Choose a finite lift $V$ of the first non-zero window of
$\gr_F(\mathcal{A})$.  For every $N$, the completed free chiral
algebra on $V$ maps to the finite quotient $\mathcal{A}_{\le N}$, and
the kernel has quadratic initial ideal $I_{2,\le N}$.  The
finite-window Maurer--Cartan elements give compatible coderivations on
\[
\bigl(\widehat{T}_{\mathrm{ch}}(V)/\overline{(I_2)}\bigr)_{\le N},
\]
so their inverse limit defines the completed curved $A_\infty$
operations on $\mathcal{A}_{\mathrm{curv}}$.

Hypothesis~(3) is stronger than filtered PBW.  Modulo the closed ideal
generated by $I_{2,\le N}$, the residual relation class is represented
by the image $\mu_{0,\le N}$ of a single central zero-ary cycle.  The
classes $\{\mu_{0,\le N}\}_N$ are compatible under the quotient maps,
so they define
\[
\mu_0=\varprojlim_N\mu_{0,\le N}\in F^2Z(\mathcal{A}).
\]
This is the finite-window convergence statement: modulo
$F^{N+1}\mathcal{A}$ only finitely many components of the completed
Maurer--Cartan element contribute, because the strong filtration gives
\(\mu_r(\bar{\mathcal{A}}^{\otimes r})\subset F^r\mathcal{A}\).

The low curved identities of
Definition~\ref{def:curved-ainfty} and
Theorem~\ref{thm:curvature-central} give
\begin{equation}\label{eq:fc-curved-identity}
\mu_1(\mu_0)=0,\qquad
\mu_1^2(a)=\mu_2(\mu_0,a)-\mu_2(a,\mu_0)=[\mu_0,a]_{\mu_2}.
\end{equation}
Since $\mu_0$ is central, the internal operator $\mu_1$ is
square-zero.  This is the square of the internal unary operation, not
the assertion that the raw curved bar construction has become
uncurved.  The ordinary bar differential is square-zero only on the
strict surface supplied by a curvature-killing Maurer--Cartan twist or
by the period-corrected total operator of
Theorem~\ref{thm:central-implies-strict}.  Without that choice, the
object is a curved CDG object and its comparison is interpreted in the
second-kind coderived category.

The finite-stage morphisms
$\mathcal{A}_{\mathrm{curv},\le N}\to\mathcal{A}_{\le N}$ induce the
identity on associated graded objects.  The spectral sequence of a
finite filtered window therefore gives a quasi-isomorphism at each
stage after a square-zero total differential has been chosen.  For the
completed ordinary comparison, apply the Milnor exact sequence to the
cone tower.  The $\varprojlim^1$ term vanishes under the
Mittag--Leffler hypothesis, and finite-dimensional cohomology groups
give this stabilization by descending-chain stabilization of images.
The completed morphism is then a filtered quasi-isomorphism.  Without
the square-zero total choice the same inverse system lives in the raw
curved CDG ambient; the cones are coacyclic, which is the Positselski
replacement for ordinary acyclicity.
\end{proof}

\begin{remark}[Algebra--cooperad passage]
Proposition~\ref{prop:filtered-to-curved-fc} is the algebra-side input
for Theorem~\ref{thm:filtered-to-curved}: finite-dimensional windows
allow continuous duality to pass the curved model from algebras to
cooperads.  The convergence mechanism is the finite-window completion
of Theorem~\ref{thm:completion-convergence}, with the discrete
conilpotent boundary supplied by
Theorem~\ref{thm:conilpotency-convergence}.
\end{remark}

\begin{remark}[Object firewall]\label{rem:filtered-curved-object-firewall}
The completed bar object, the coalgebraic Koszul object, the Koszul
dual algebra, bar--cobar inversion, and the derived chiral centre are
five different constructions.
On the finite-window lane
\[
\widehat{\bar B}_X(\mathcal A)
=\varprojlim_N\bar B_X(\mathcal A_{\le N})
\]
is the completed bar coalgebra.  Its coalgebraic Koszul object is
\[
\mathcal A^{\mathrm i}_{\mathrm{cpl}}
:=H^\bullet(\widehat{\bar B}_X(\mathcal A))
\]
when that cohomology carries the required completed coalgebra
structure.  The algebraic Koszul dual is obtained only after Verdier
duality on the Ran space and cobar:
\[
\mathcal A^!_\infty
:=\Omega_X\bigl(\mathbb D_{\Ran}\widehat{\bar B}_X(\mathcal A)\bigr),
\]
under the finiteness hypotheses of
Construction~\ref{const:completed-koszul}.  The counit
\[
\widehat\Omega_X(\widehat{\bar B}_X(\mathcal A))\longrightarrow
\mathcal A
\]
is bar--cobar inversion, as in
Theorem~\ref{thm:completed-bar-cobar}; it recovers $\mathcal A$, not
$\mathcal A^!$.  The derived chiral centre is instead
\[
Z^{\mathrm{der}}_{\mathrm{ch}}(\mathcal A)
=C^\bullet_{\mathrm{ch}}(\mathcal A,\mathcal A),
\]
the Hochschild closed-sector complex acting on~$\mathcal A$.  It is not a bar
coalgebra, not $\mathcal A^{\mathrm i}_{\mathrm{cpl}}$, and not
$\mathcal A^!_\infty$.
\end{remark}

\begin{example}[Virasoro: central curvature, auxiliary filtration]\label{ex:vir-filtered-to-curved-fc}
The Virasoro OPE is
\[
T(z)T(w)\sim
\frac{c/2}{(z-w)^4}
+\frac{2T(w)}{(z-w)^2}
+\frac{\partial T(w)}{z-w}.
\]
The quartic pole is the central scalar direction; in the higher-genus
curved model its coefficient is the curvature coefficient.  In the
normalization of the landscape census,
\[
\kappa(\mathrm{Vir}_c)=c/2.
\]
The precise representative of $\mu_0$ depends on the chosen
$A_\infty$ model, but its modular characteristic is the central scalar
$c/2$ and its target is the vacuum line.  The weight-$4$ quasi-primary
\[
\Lambda={:}TT{:}-\frac{3}{10}\partial^2T
\]
is a composite in the envelope of the single strong generator $T$; it
is not an independent strong generator.  Thus the conformal-weight
filtration is auxiliary for the Virasoro curved lane, while completion
records the infinite descendant tower.
\end{example}

\begin{example}[\texorpdfstring{$W_3$}{W3}: intrinsic finite-window filtration]\label{ex:w3-not-curved-fc}
The algebra $\mathcal{W}_3$ has strong generators $L$ and $W$ of
weights $2$ and $3$.  The $W$--$W$ OPE has a sixth-order scalar pole
and non-linear composite fields, including ${:}LL{:}$.  Its scalar
modular characteristic is
\[
\kappa(\mathcal{W}_3)=5c/6,
\]
but the non-descendant composites are not generated by a single
central zero-ary curvature element.  Hence the central curved
reduction of Proposition~\ref{prop:filtered-to-curved-fc} does not
describe the full algebra.  The correct object is the completed
finite-window bar coalgebra
\[
\widehat{\bar B}(\mathcal W_3)
=\varprojlim_N \bar B\bigl((\mathcal W_3)_{\le N}\bigr),
\]
with convergence controlled by the strong filtration and the
Mittag--Leffler tower.
\end{example}

\begin{example}[Heisenberg: discrete quadratic endpoint]
For the rank-one Heisenberg algebra,
\[
J(z)J(w)\sim\frac{k}{(z-w)^2},\qquad
\kappa(\mathcal H_k)=k.
\]
There is no simple-pole bracket channel and no independent composite
generator.  The reduced bar coalgebra is conilpotent by bar length,
so genus-$0$ bar--cobar inversion is discrete.  Higher-genus curvature
is central and scalar; finite-window completion changes no finite bar
word.
\end{example}

\begin{theorem}[Finite-window convergence in the filtered and curved regimes; \ClaimStatusProvedHere]\label{thm:bar-convergence-fc}
Let $\mathcal{A}$ be an augmented positive-energy chiral $A_\infty$
algebra.  In the completed cases below, assume that the chosen
finite-window filtration is separated, complete, strong in the sense
of Definition~\ref{idea:I-adic}, and has finite-dimensional conformal
windows.  The convergence surface is determined as follows.
\begin{enumerate}
\item If the reduced bar coalgebra is discrete finite-type and
conilpotent, the bar--cobar comparison is governed by
Theorem~\ref{thm:conilpotency-convergence}; no completion is needed,
and $\Omega_X(\bar B_X(\mathcal A))\to\mathcal A$ is inversion.
\item If $\mathcal{A}$ satisfies
Proposition~\ref{prop:filtered-to-curved-fc}, the completed curved bar
construction converges in the finite-window topology.  Central
curvature gives $\mu_1^2=0$ for the internal unary operator.  The
ordinary bar differential is square-zero only after a
curvature-killing Maurer--Cartan twist or after passage to the
period-corrected total model.  Without such a strictification, the
comparison belongs to the completed coderived CDG category.
\item If the strong finite-window filtration holds but the
central-curvature closure fails, convergence is exactly the
completion theorem
\[
\widehat{\bar B}(\mathcal A)=\varprojlim_N\bar B(\mathcal A_{\le N})
\]
of Theorem~\ref{thm:completion-convergence}.  The finite-stage
cohomology tower must satisfy Mittag--Leffler for ordinary cohomology
to commute with the inverse limit.  The algebra $\mathcal W_3$ lies in
this lane.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(1) is the finite-type conilpotent clause of
Theorem~\ref{thm:conilpotency-convergence}.  Part~(2) is
Proposition~\ref{prop:filtered-to-curved-fc} together with
Theorem~\ref{thm:curvature-central}: central curvature kills the
internal commutator $[\mu_0,-]$, while
Theorem~\ref{thm:central-implies-strict} identifies the extra datum
needed for an ordinary square-zero bar differential.  The completed
bar construction still remembers the curvature through its twisting
cochain and through the CDG structure.  If centrality fails, the
identity $m_1^2=[\mu_0,-]_{\mu_2}$ is already nonzero at the raw
curved level; ordinary cohomology is not the invariant, and
Positselski's coderived category is.

For Part~(3), the strong finite-window hypothesis makes every finite
quotient $\mathcal A_{\le N}$ a finite bar--cobar problem and makes
the completed Maurer--Cartan equation finite in each window.  Passing
from finite windows to the inverse limit is precisely
Theorem~\ref{thm:completion-convergence}; the Milnor obstruction is
the $\varprojlim^1$ term, which vanishes under the stated
Mittag--Leffler condition.  Construction~\ref{const:completed-koszul}
then supplies the object firewall:
$\widehat{\bar B}_X(\mathcal A)$ is the completed bar coalgebra,
$\mathcal A^{\mathrm i}_{\mathrm{cpl}}$ is its coalgebraic Koszul
cohomology when defined, $\mathcal A^!_\infty$ requires the Verdier
step, and $\widehat\Omega_X(\widehat{\bar B}_X(\mathcal A))\to
\mathcal A$ is inversion.  The derived chiral centre
$Z^{\mathrm{der}}_{\mathrm{ch}}(\mathcal A)
=C^\bullet_{\mathrm{ch}}(\mathcal A,\mathcal A)$ is the Hochschild
bulk complex and is not produced by any of those three operations.  The
$W$--$W$ OPE of $\mathcal W_3$
contains non-descendant composites in the finite-window tower, so
Proposition~\ref{prop:filtered-to-curved-fc} does not apply to its
full algebra, but the completed finite-window theorem does.
\end{proof}

\begin{remark}[Regime criterion]\label{rem:regime-criterion-fc}
For a non-quadratic algebra, the regime is determined by four
mathematical tests.
\begin{enumerate}
\item If the reduced bar coalgebra is finite-type and conilpotent, use
the discrete bar--cobar comparison.
\item If all non-quadratic relation classes are quadratic consequences
plus one central zero-ary curvature element, use the central curved
finite-window model.
\item If non-descendant composites occur in arbitrarily high windows,
use the completed finite-window bar coalgebra.
\item If the generating space itself is infinite-type, the finite-type
theorems here do not apply until a strong completion tower supplies
finite windows.
\end{enumerate}
\end{remark}
