\chapter{Chiral Hochschild cohomology and deformation theory}

\index{Hochschild cohomology!classical}
\index{cyclic homology!chiral}
\index{three Hochschild theories!disjoint discipline}

\begin{remark}[Chiral, topological, categorical Hochschild are
disjoint]
\label{rem:hh-three-theories-discipline}

The three Hochschild theories occurring in the programme are not
interchangeable. The chiral Hochschild $\ChirHoch^*(\cA)$ takes a
chiral algebra on a curve $X$ as input and outputs an object
of cohomological amplitude~$[0,2]$ on the Koszul locus
\textup{(}Theorem~H, see Theorem~\textup{\ref{thm:main-koszul-hoch}}
in Chapter~\textup{\ref{chap:deformation-theory}}\textup{)}. The
topological Hochschild homology $\mathrm{THH}(R)$ takes an
$E_1$-ring spectrum and outputs an $S^1$-equivariant spectrum.
Its classical algebraic cochain shadow for a discrete or dg algebra
$A$ is $\mathrm{HH}^\bullet_{\mathrm{alg}}(A)=\RHom_{A^e}(A,A)$.
The categorical Hochschild $\mathrm{HH}^*_{\mathrm{cat}}$ takes a
dg category and outputs an $E_2$-algebra carrying CY shifted Poisson
structure. The geometry selects which Hochschild: a curve produces
$\ChirHoch^*$, a circle-spectrum trace produces $\mathrm{THH}$, a
pointed dg algebra produces $\mathrm{HH}^\bullet_{\mathrm{alg}}$,
and a CY dg category produces $\mathrm{HH}^*_{\mathrm{cat}}$.
The present chapter works exclusively with $\ChirHoch^*$; the other
theories appear only in explicit comparison statements
\textup{(}Theorem~\textup{\ref{thm:hochschild-classical-comparison}}
records the spectral sequence relating
$\mathrm{HH}^\bullet_{\mathrm{alg}}$ at the fibre to
$\ChirHoch^*$ on the curve\textup{)}.
\end{remark}

The chiral Hochschild cohomology $\ChirHoch^*(\cA)$ is the
tangent complex to the MC moduli at~$\Theta_\cA$: the cohomology
of the convolution $L_\infty$-algebra controlling deformations,
obstructions, and bulk-field couplings.

The chiral Hochschild complex carries a degree $-1$ Lie bracket
(the chiral Gerstenhaber bracket, Theorem~\ref{thm:gerstenhaber-structure}),
computed by OPE residues on FM configuration spaces.
In the classical limit (fiber at a point), it recovers
Gerstenhaber's bracket~\cite{Ger63} on associative Hochschild
cochains. The chiral bracket is the strict shadow of a full
$L_\infty$ bracket on the chiral Hochschild complex. In the
classical algebraic strict model,
$\mathrm{HH}^2_{\mathrm{alg}}$ classifies first-order
deformations and $\mathrm{HH}^3_{\mathrm{alg}}$ contains
obstructions;
the $L_\infty$ extension records coherent homotopies governing
convergence of formal deformations and transfer of Koszul properties
across quasi-isomorphisms. The cyclic structure (Connes'
operator~$B$, the mixed complex, the SBI sequence) is the algebraic
shadow of the modular operad's gluing maps. The shadow obstruction
tower of Chapter~\ref{sec:koszul-across-genera} projects onto the
cyclic deformation complex
$\mathrm{Def}_{\mathrm{cyc}}^{\mathrm{mod}}(\cA)$ defined here.

For all chirally Koszul algebras, $\ChirHoch^n(\cA) = 0$ for
$n > 2$ (Theorem~H): the Heisenberg has $P(t) = 1 + t + t^2$;
the Virasoro and principal W-algebras have $P(t) = 1 + t^2$ at
generic level (Theorems~\ref{thm:virasoro-hochschild}
and~\ref{thm:w-algebra-hochschild}).

The fiberwise curvature $\dfib^{\,2} = \kappa(\cA) \cdot \omega_1$ at
genus~$1$ (Chapter~\ref{ch:heisenberg-frame}) shows that deformations
of the bar complex are controlled by a cohomological invariant.
Chiral Hochschild cohomology organizes these deformations and obstructions
into a single graded object equipped with a Gerstenhaber bracket;
the chiral enhancement incorporates OPE data, the geometry of the
curve, and the $A_\infty$ structure of the bar complex.

\begin{remark}[Conventions for HH/HC/HP]
\label{rem:hh-hc-canonical-source}
\index{Hochschild cohomology!canonical conventions}
\index{cyclic homology!canonical conventions}
\index{periodic cyclic homology!canonical conventions}
The definitions and sign conventions for classical algebraic
Hochschild cohomology $\mathrm{HH}^\bullet_{\mathrm{alg}}$,
classical algebraic Hochschild homology
$\mathrm{HH}_{\bullet,\mathrm{alg}}$, cyclic homology
$\mathrm{HC}_*$, negative cyclic homology $\mathrm{HC}_*^{\mathrm{neg}}$,
and periodic cyclic homology $\mathrm{HP}_*$ are as follows. In particular:
\begin{itemize}
\item the chiral Hochschild complex
 (Definition~\ref{def:chiral-hochschild}),
\item the cyclic operator and Connes' operator~$B$
 (Definitions~\ref{def:cyclic-operator} and~\ref{def:connes-B}),
\item the mixed complex $(d_{\mathrm{HH}}, B)$ and the SBI exact
 sequence (Theorem~\ref{thm:connes-exact-sequence},
 Corollary~\ref{cor:connes-SBI}),
\end{itemize}
are all defined here and should be cited from here throughout the text.
Other chapters that use chiral Hochschild, topological Hochschild
homology, or cyclic invariants
\textup{(}the deformation theory and Poincar\'e duality chapters\textup{)}
reference these definitions rather than re-establishing them.
\end{remark}

\section{Classical to chiral}

\subsection{Review of classical Hochschild}

For an associative algebra $A$ over $\mathbb{C}$ and an
$A$-bimodule~$M$, the classical algebraic Hochschild cohomology
$\mathrm{HH}^\bullet_{\mathrm{alg}}(A, M) = \mathrm{Ext}^*_{A^e}(A, M)$
classifies the deformation theory of~$A$:
$\mathrm{HH}^0_{\mathrm{alg}}$ is the center,
$\mathrm{HH}^1_{\mathrm{alg}}$ classifies outer derivations,
$\mathrm{HH}^2_{\mathrm{alg}}$ classifies first-order deformations,
and $\mathrm{HH}^3_{\mathrm{alg}}$ contains the obstructions to
extending them. The full structure is computed by the bar resolution
$\cdots \to A^{\otimes(n+2)} \xrightarrow{b} A^{\otimes(n+1)} \to
\cdots$ with differential $b(a_0 \otimes \cdots \otimes a_{n+1})
= \sum_{i=0}^n (-1)^i a_0 \otimes \cdots \otimes a_ia_{i+1}
\otimes \cdots \otimes a_{n+1}$, and the resulting cohomology
carries a Gerstenhaber bracket governing the Maurer--Cartan equation
for formal deformations \textup{(}Gerstenhaber~\cite{Ger63}\textup{)}.

\subsection{Chiral enhancement}

What replaces the bimodule $A \otimes A^{\mathrm{op}}$ when the algebra lives on a curve rather than a point? For chiral algebras, each ingredient of the classical theory acquires a geometric upgrade: the bimodule structure is replaced by the factorization structure on~$\operatorname{Ran}(X)$, the bar resolution becomes the geometric bar complex on Fulton--MacPherson configuration spaces, and the Gerstenhaber bracket lifts to a chiral bracket governed by the OPE. The result is a chiral Hochschild complex whose cohomology computes chiral deformations, obstructions, and the center of the chiral algebra simultaneously.

\begin{definition}[Chiral Hochschild complex, derived-functor form]
\label{def:chiral-hochschild-derived}
For a chiral algebra $\mathcal{A}$ on $X$, the chiral Hochschild
cohomology with coefficients in a chiral $\mathcal{A}$-module
$\mathcal{M}$ is
\[\ChirHoch^*(\mathcal{A}, \mathcal{M})
= \operatorname{RHom}_{\mathcal{D}_X}(\barBgeom(\mathcal{A}), \mathcal{M}).\]
The chain-level model is Definition~\ref{def:chiral-hochschild}.
\end{definition}

\begin{theorem}[Comparison with classical theory {\cite{BD04}}; \ClaimStatusProvedElsewhere]\label{thm:hochschild-classical-comparison}
There is a spectral sequence:
\[
E_2^{p,q}
= \mathrm{HH}^p_{\mathrm{alg}}(\mathcal{A}_0, H^q(\Omega^*_X))
\Rightarrow \ChirHoch^{p+q}(\mathcal{A})
\]
where $\mathcal{A}_0$ is the fiber at a point.
\end{theorem}

\section{Periodicity phenomena}

\subsection{Virasoro chiral Hochschild cohomology}

\begin{theorem}[Virasoro chiral Hochschild cohomology; \ClaimStatusProvedHere]\label{thm:virasoro-hochschild}
For the Virasoro algebra at generic central charge $c$ (avoiding
$c_{p,q} = 1 - 6(p-q)^2/(pq)$ and $c = 1$):
\[\ChirHoch^n(\mathrm{Vir}_c) = \begin{cases}
\mathbb{C} & n = 0 \text{ (center: scalars)}, \\
0 & n = 1 \text{ (no outer derivations at generic $c$)}, \\
\mathbb{C} & n = 2 \text{ (central charge deformation)}, \\
0 & n \geq 3.
\end{cases}\]
The Hilbert series is $P(t) = 1 + t^2$.
\end{theorem}

\begin{proof}
The Virasoro algebra is chirally Koszul
(Corollary~\ref{cor:universal-koszul}: freely strongly generated
implies bar concentration). Theorem~H
(Theorem~\ref{thm:hochschild-polynomial-growth}) gives concentration:
$\ChirHoch^n(\mathrm{Vir}_c) = 0$ for $n \notin \{0, 1, 2\}$,
since the de~Rham functor on a curve has cohomological
amplitude~$[0,2]$.

For the individual degrees:
$\ChirHoch^0(\mathrm{Vir}_c) = Z(\mathrm{Vir}_c) = \mathbb{C}$
(the center at generic~$c$ is one-dimensional: only scalars commute
with all modes).
$\ChirHoch^1(\mathrm{Vir}_c) = 0$: at generic~$c$, every Verma
module $V(c,h)$ is irreducible (Kac determinant nonvanishing), so all
derivations of $\mathrm{Vir}_c$ are inner.
$\ChirHoch^2(\mathrm{Vir}_c) = \mathbb{C}$: by the Koszul duality
exchange (Theorem~\ref{thm:main-koszul-hoch}),
$\dim \ChirHoch^2(\mathrm{Vir}_c) = \dim Z(\mathrm{Vir}_{26-c}) = 1$.
The generator is the central charge deformation $c \mapsto c + \epsilon$.
\end{proof}

\begin{remark}[Relation to Gel'fand--Fuchs cohomology]
\label{rem:gf-vs-chirhoch}
The continuous Lie algebra cohomology
$H^*_{\mathrm{cont}}(L_1; \mathbb{C}) = \mathbb{C}[\Theta]$ is a
polynomial ring on a degree-$2$ generator
(Gel'fand--Fuchs~\cite{Fuks86}). This is \emph{not} the
chiral Hochschild cohomology $\ChirHoch^*(\mathrm{Vir}_c)$: the former is
the cohomology of a topological Lie algebra (no curve geometry),
while the latter is an Ext-group on the curve~$X$ that inherits the
de~Rham amplitude bound $[0, 2\dim X] = [0, 2]$ from the
$\mathcal{D}_X$-module structure. The two are related by a
spectral sequence
(Theorem~\ref{thm:hochschild-classical-comparison}), but the
Gel'fand--Fuchs polynomial ring in all even degrees truncates to
the $\{0, 1, 2\}$~range when passing to the chiral Hochschild
cohomology on a curve.
\end{remark}

\subsection{Affine Kac--Moody periodicity}

\begin{theorem}[Critical level Lie algebra cohomology; \ClaimStatusProvedElsewhere]\label{thm:critical-level-cohomology}
The continuous Lie algebra cohomology of $\widehat{\mathfrak{g}}$ at critical level $k = \critLevel$ is the exterior-polynomial algebra
\[H^*_{\mathrm{cont}}(\widehat{\mathfrak{g}}_{\critLevel},
\widehat{\mathfrak{g}}_{\critLevel,0};\, \mathbb{C})
\;\cong\; \Lambda^*(P_1,\ldots,P_r) \otimes \mathbb{C}[\Theta_1,\ldots,\Theta_r]\]
with $\deg P_i = 2m_i + 1$ and $\deg \Theta_i = 2(m_i+1)$, where $m_1,\ldots,m_r$ are the exponents of~$\mathfrak{g}$ (Fuks--Feigin--Tsygan~\cite{FT87}, via BD comparison~\cite{BD04}). For rank~$1$ ($\mathfrak{sl}_2$): $H^{n+4} \cong H^n$ (strict periodicity). For rank $r > 1$: polynomial growth $O(n^{r-1})$ without strict periodicity (Theorem~\ref{thm:affine-periodicity-critical}).
\end{theorem}

\begin{remark}[Critical level: Lie cohomology vs chiral Hochschild]
\label{rem:critical-level-lie-vs-chirhoch}
At \emph{generic} level ($k \neq -h^\vee$), chiral Hochschild
cohomology and continuous Lie algebra cohomology are different
functors: Theorem~H
(Theorem~\ref{thm:hochschild-polynomial-growth})
bounds $\ChirHoch^n = 0$ for $n > 2$, while the Lie algebra
cohomology extends into arbitrarily high degrees.

At \emph{critical} level ($k = -h^\vee$), chiral Koszulness
fails: PBW degeneration (Proposition~\ref{prop:pbw-universality})
still holds, but the Ext algebra $\mathrm{Ext}^{p,q}$ is not
diagonally concentrated (the Feigin--Frenkel center
$\mathrm{Fun}(\mathrm{Op})$ lives at bar degree $p = 0$ with
conformal weight $q > 0$). Since Theorem~H requires diagonal
Ext concentration (via bar concentration,
Theorem~\ref{thm:bar-concentration}), Theorem~H does not apply
at critical level.

Instead, the Beilinson--Drinfeld chiral-envelope comparison
(\cite[Theorem~4.8.1]{BD04}, specialised to the affine Lie-$*$ algebra
$\fg \otimes \omega_X$ at critical level and combined with the
Feigin--Frenkel identification of the chiral centre
\cite{Feigin-Frenkel}) identifies the chiral Hochschild
cohomology with the continuous Lie algebra cohomology:
\[
\ChirHoch^*(\widehat{\fg}_{-h^\vee})
\;\cong\;
H^*_{\mathrm{Lie,cont}}(\fg \otimes t\bC[[t]];\, \bC)
\;\cong\;
\Lambda^*(P_1, \ldots, P_r) \otimes \bC[\Theta_1, \ldots, \Theta_r],
\]
which is \emph{unbounded} with polynomial growth $O(n^{r-1})$
(Theorem~\ref{thm:affine-periodicity-critical}). In particular,
$\dim \ChirHoch^0 = \infty$ (the Feigin--Frenkel center), and
$\dim \ChirHoch^n = \infty$ for all~$n \geq 0$.

Summary: at generic level, ChirHoch is bounded in $\{0, 1, 2\}$
and differs from Lie cohomology above degree~$2$; at critical
level, the BD comparison identifies them, and ChirHoch is
unbounded.
\end{remark}

The exterior-polynomial structure of the Lie algebra cohomology
arises from the Coxeter element $w_{\mathrm{Cox}} \in W$ acting on the center at critical level (Feigin--Frenkel~\cite{Feigin-Frenkel}; the exterior-polynomial decomposition follows from Feigin--Frenkel's description of the center $\mathfrak{z}(\widehat{\mathfrak{g}})$ at critical level~\cite{Feigin-Frenkel}). For simply-laced~$\mathfrak{g}$, $\mathsf{h} = h^\vee$; for non-simply-laced~$\mathfrak{g}$, $\mathsf{h} \neq h^\vee$ in general.

\subsection{W-algebra chiral Hochschild cohomology}

For W-algebras at generic level, Theorem~H gives concentration in $\{0, 1, 2\}$:

\begin{theorem}[W-algebra chiral Hochschild cohomology; \ClaimStatusProvedHere]\label{thm:w-algebra-hochschild}
For the principal W-algebra $\Walg^k(\mathfrak{g}) = \Walg^k(\mathfrak{g}, f_{\mathrm{prin}})$ at generic level $k$
(away from admissible and critical levels), the chiral Hochschild cohomology
is concentrated in degrees $\{0, 1, 2\}$:
\[\ChirHoch^n(\Walg^k(\mathfrak{g})) = 0 \quad \text{for } n \notin \{0, 1, 2\}.\]
The nonvanishing degrees are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\ChirHoch^0(\Walg^k(\mathfrak{g})) = Z(\Walg^k(\mathfrak{g})) = \mathbb{C}$
 \textup{(}the center at generic~$k$ is one-dimensional\textup{)};
\item $\ChirHoch^1(\Walg^k(\mathfrak{g})) = 0$ at generic~$k$
 \textup{(}the Shapovalov form is non-degenerate, all derivations are
 inner\textup{)};
\item $\ChirHoch^2(\Walg^k(\mathfrak{g})) = \mathbb{C}$
 \textup{(}the level deformation; equivalently,
 $\dim Z((\Walg^k(\mathfrak{g}))^!) = 1$ by
 Theorem~\textup{\ref{thm:main-koszul-hoch})}.
\end{enumerate}
The Hilbert series is $P(t) = 1 + t^2$.
\end{theorem}

\begin{proof}
The argument has two parts: concentration from Theorem~H, and
identification of the individual degrees.

\emph{Step 1} (Concentration).
By the Feigin--Frenkel free-field realization, the universal
W-algebra $\Walg^k(\mathfrak{g})$ is freely strongly generated by
$r = \mathrm{rank}(\mathfrak{g})$ fields of conformal weights
$h_i = m_i + 1$. Corollary~\ref{cor:universal-koszul} gives chiral
Koszulness. Theorem~H (Theorem~\ref{thm:hochschild-polynomial-growth})
then gives $\ChirHoch^n = 0$ for $n \notin \{0, 1, 2\}$.

\emph{Step 2} (Individual degrees).
$\ChirHoch^0 = Z(\Walg^k) = \mathbb{C}$: at generic~$k$, the
W-algebra is simple (Arakawa~\cite{Ara07}, Theorem~4.1), so the
center is one-dimensional.
$\ChirHoch^1 = 0$: at generic~$k$, the Shapovalov form on Verma
modules is non-degenerate (no singular vectors), giving Ext-vanishing
and hence no outer derivations.
$\ChirHoch^2 = \mathbb{C}$: by the Koszul duality exchange
(Theorem~\ref{thm:main-koszul-hoch}),
$\dim \ChirHoch^2(\Walg^k) = \dim Z((\Walg^k)^!)$. The Koszul dual of
the principal W-algebra at generic level has one-dimensional center.
\end{proof}

\begin{remark}[Gel'fand--Fuchs cohomology vs chiral Hochschild]
\label{rem:gf-walg-vs-chirhoch}
The continuous relative cohomology of the topological Lie algebra
$\mathrm{Lie}(\Walg^k(\mathfrak{g}))$ with $r$ generating currents is a
polynomial ring
$H^*_{\mathrm{cont}}(\mathrm{Lie}(\Walg),
\mathrm{Lie}(\Walg)_0;\, \mathbb{C})
= \mathbb{C}[\Theta_1, \ldots, \Theta_r]$
with $\Theta_i \in H^{h_i}$
(Fuchs~\cite{Fuks86}, Ch.~2; Feigin--Fuchs~\cite{FF84} for $r = 1$).
This is a \emph{different} invariant from $\ChirHoch^*(\Walg^k)$:
the Gel'fand--Fuchs cohomology is the continuous Lie algebra cohomology
(without curve geometry), while the chiral Hochschild cohomology is an
Ext on the curve~$X$, bounded by the de~Rham amplitude $[0,2]$. The
polynomial ring in all degrees truncates to the
range $\{0,1,2\}$ when passing to the chiral setting on a curve.
For the Virasoro ($r = 1$): $H^*_{\mathrm{cont}}(L_1) = \mathbb{C}[\Theta]$
has Hilbert series $1/(1-t^2)$, but $\ChirHoch^*(\mathrm{Vir}_c)$ has
Hilbert series $1 + t^2$.
\end{remark}

\begin{remark}[Scope]
The concentration from Theorem~H requires chiral Koszulness, which
holds for the universal algebra $\Walg^k(\mathfrak{g})$ at all
levels (including admissible) by Feigin--Frenkel free generation.
The identification of individual degrees uses generic-level
hypotheses (Ext-vanishing, simplicity). At critical level $k =
-h^\vee$, the center enlarges to the Feigin--Frenkel center
$\mathfrak{z}(\widehat{\mathfrak{g}})$, and the computation changes
(Theorem~\ref{thm:critical-level-cohomology}).
For non-principal nilpotent orbits (Remark below), the simplicity hypothesis
requires case-by-case verification.
\end{remark}

\begin{remark}[Elementary model presentation;
Convention~\ref{conv:proof-architecture}]
\label{rem:theorem-h-model}
\index{chiral Hochschild cohomology!model presentation}
\emph{Step~A} (H-level):
$\ChirHoch^*(\cA)$ is the endomorphism algebra of the
identity functor on factorization $\cA$-modules: it classifies
$A_\infty$-deformations of the chiral algebra~$\cA$.
Concentration in $\{0,1,2\}$ (Theorem~H) asserts that
deformations live in $\ChirHoch^2$ and obstructions in
$\ChirHoch^3 = 0$: all first-order deformations are
unobstructed, and the formal moduli space is smooth.
For the principal W-algebra at generic level:
$\dim \ChirHoch^2(\Walg^k(\fg)) = 1$ (the level
deformation $k \mapsto k + \epsilon$).

\emph{Step~B} (M-level):
The proof uses the Koszul resolution: the bar-cobar
quasi-isomorphism (Theorem~B on the Koszul locus) provides
a resolution of $\cA$ by free chiral algebras generated from
$\cA^!$. The Hom complex computing the Ext groups is a
complex of $\mathcal{D}_X$-module morphisms on the
curve~$X$. The de~Rham amplitude bound
$[0, 2\dim X] = [0,2]$ gives concentration.

\emph{Reduction B$\to$A} (M-level $\to$ H-level):
The M-level bar complex
$\bar{B}_{\mathrm{HH}}(\cA) = (\cA \otimes T^c(s^{-1}\bar\cA)
\otimes \cA,\, d)$ is a dg model for the derived endomorphism
object $R\!\operatorname{End}_{\cA\text{-}\cA}(\cA)$.
By Proposition~\ref{prop:model-independence}, the H-level
endomorphism algebra is recovered from the M-level bar complex
up to contractible ambiguity.

\emph{Step~C} (S-level):
The Hilbert series is $P_{\Walg^k(\fg)}(t) = 1 + t^2$ at
generic level: $\ChirHoch^0 = \bC$ (center),
$\ChirHoch^1 = 0$ (no outer derivations), $\ChirHoch^2 = \bC$
(level deformation).

\emph{Reduction B$\to$C} (M-level $\to$ S-level):
The S-level Hilbert series is extracted from the M-level
concentration: the vanishing $\ChirHoch^n = 0$ for $n > 2$
(Theorem~H) determines the Hilbert polynomial as a
degree-$2$ polynomial in~$t$.
\end{remark}

\begin{remark}[Non-principal nilpotent orbits]
For general $\Walg^k(\mathfrak{g}, f)$ with $f$ not necessarily principal, the conformal weights of the generators are determined by the Kazhdan grading associated to the $\mathfrak{sl}_2$-triple $(e, h, f)$. The concentration $\ChirHoch^n = 0$ for $n > 2$ holds whenever the algebra is chirally Koszul (Theorem~H); the individual dimensions $\dim \ChirHoch^0$, $\dim \ChirHoch^1$, $\dim \ChirHoch^2$ depend on the center, derivations, and Koszul dual center for the specific orbit. For special orbits where Koszulness is open, the concentration bound remains conjectural.
\end{remark}

\section{Deformation theory}

\subsection{Infinitesimal deformations}

\begin{theorem}[Deformation classification {\cite{Ger63,Loday98}}; \ClaimStatusProvedElsewhere]\label{thm:deformation-classification}
\begin{enumerate}
\item $\ChirHoch^1(\mathcal{A})$ classifies \emph{outer derivations} $\mathrm{Der}(\mathcal{A})/\mathrm{Inn}(\mathcal{A})$ (not infinitesimal automorphisms, which are all derivations).
\item $\ChirHoch^2(\mathcal{A})$ classifies first-order deformations.
\item $\ChirHoch^3(\mathcal{A})$ contains the primary obstructions to extending deformations.
\item Unobstructed deformations correspond to marginal operators in CFT.
\end{enumerate}
\end{theorem}

\begin{example}[Marginal deformations of beta-gamma]
For the $\beta\gamma$ system:
\[\ChirHoch^2(\beta\gamma) = \mathbb{C} \cdot [\beta\gamma]\]
The class $[\beta\gamma]$ corresponds to the exactly marginal operator changing the conformal weights.
\end{example}

\subsection{Formal deformation theory}

The formal deformation space is controlled by the differential graded Lie algebra
$\mathfrak{g}_{\mathcal{A}} = \ChirHoch^*(\mathcal{A}, \mathcal{A})[1]$
with the Gerstenhaber bracket.

\begin{theorem}[Maurer--Cartan equation {\cite{Kon03,KontsevichSoibelman}}; \ClaimStatusProvedElsewhere]\label{thm:maurer-cartan-deformations}
Formal deformations correspond to solutions of:
\[d\alpha + \frac{1}{2}[\alpha, \alpha] = 0, \quad \alpha \in \mathfrak{g}_{\mathcal{A}}^1\]
\end{theorem}

\section{Physical applications}

\subsection{Marginal operators and RG flow}

In CFT, marginal operators have dimension $(1,1)$ and correspond to
$\ChirHoch^2_{\text{marginal}}(\mathcal{A}) = \{\omega \in \ChirHoch^2 : h(\omega) = 1\}$.
The beta function vanishes if and only if the obstruction in $\ChirHoch^3$ vanishes.

\subsection{String field theory}

The conjectural identification of the bar complex with BRST cohomology (Conjecture~\ref{conj:master-bv-brst}) takes the form:
\[H^*_{\text{BRST}}(\text{String}[\mathcal{A}]) \cong \ChirHoch^*(\mathcal{A})\]

String vertices are encoded in the $A_\infty$ structure: $m_2$ gives the three-string vertex, $m_3$ the four-string contact term, and higher $m_k$ the multi-string interactions.

\section{Computational tools}

\subsection{Spectral sequences}

\begin{theorem}[Bar spectral sequence {\cite{BD04,CG17}}; \ClaimStatusProvedElsewhere]\label{thm:bar-spectral-sequence-hochschild}
\[E_1^{p,q} = H^q(\ConfigSpace{p}(X), \mathcal{A}^{\boxtimes p}) \Rightarrow \ChirHoch^{p+q}(\mathcal{A})\]
\end{theorem}

\subsection{Explicit computations}

For the Heisenberg algebra:
\[\ChirHoch^n(\text{Heis}_k) = \begin{cases}
\mathbb{C} & n = 0 \text{ (center: only scalars commute with all of } \text{Heis}_k) \\
\mathbb{C} & n = 1 \text{ (outer derivation } D(\alpha)=\mathbf{1}\text{; zero mode is central)} \\
\mathbb{C} & n = 2 \text{ (central extension: the level deformation)} \\
0 & n \geq 3
\end{cases}\]

For free fermions (with OPE $\psi(z)\psi^*(w) \sim (z-w)^{-1}$):
\[\ChirHoch^n(\text{Fermions}) = \begin{cases}
\mathbb{C} & n = 0 \text{ (center: only scalars)} \\
0 & n = 1 \text{ (all derivations of the Clifford algebra are inner)} \\
\mathbb{C} & n = 2 \text{ (one-dimensional deformation space)}
\end{cases}\]
(The computation follows from the Clifford algebra structure:
$\mathrm{HH}^0_{\mathrm{alg}}$ is the center $\mathbb{C}$;
$\mathrm{HH}^1_{\mathrm{alg}} = 0$ by the standard result that all
derivations of a Clifford algebra are inner \cite[Ch.~9]{Weibel94};
$\mathrm{HH}^2_{\mathrm{alg}} \cong \mathbb{C}$ represents the unique
deformation parametrized by the level.)
\section{Chiral Hochschild-cyclic spectral sequence for chiral algebras}
\label{sec:hochschild-cyclic-spectral}

\begin{remark}[Physical origin]
In 2d~CFT on a genus~$g$ surface $\Sigma_g$, the partition function
$Z[\Sigma_g] = \operatorname{Tr}_{\mathcal{H}}(q^{L_0-c/24})$ is
related to the chiral Hochschild-cyclic spectral sequence: the $E_1$ page
gives the tree-level (genus~$0$) contribution, $E_2$ incorporates
one-loop corrections, and higher pages capture multi-loop effects.
For chirally Koszul algebras at generic level, the spectral sequence
degenerates at~$E_2$ by the Ext-vanishing argument
(Theorem~\ref{thm:w-algebra-hochschild}).
\end{remark}

\begin{construction}[Geometric realization via loop spaces]
The chiral Hochschild complex of a chiral algebra $\mathcal{A}$ on a curve $X$ is:
\[\text{HC}_n^{\text{ch}}(\mathcal{A}) = \Gamma(C_n(X), 
 \mathcal{A}^{\boxtimes n} \otimes \det(\Omega^1_{C_n(X)/X}))\]

This has a natural $S^1$-action (cyclic rotation of points), giving:
\[\text{HC}_n^{\text{ch}}(\mathcal{A}) = 
 [\text{Maps}(S^1, LX) \otimes_{\mathcal{A}} \mathcal{A}^{\otimes n}]^{S^1}\]
where $LX = \text{Maps}(S^1, X)$ is the loop space.

The cyclic spectral sequence computes $H_*(LX, \mathcal{A})$ by first computing 
$H_*(\text{Maps}(S^1, X), \mathcal{A})$ and then taking $S^1$-invariants.

Chiral Hochschild homology computes the homology of the free loop space, and cyclic homology computes the $S^1$-equivariant loop space homology.
This identification is classical for associative algebras \cite{Loday98}; the chiral extension follows from the factorization structure of the loop space \cite[Chapter~5]{CG17}.
\end{construction}

\begin{computation}[Explicit second-page computation; \ClaimStatusProvedHere]
We compute the $E_2$ page explicitly for standard examples:

\emph{Heisenberg algebra.}
\[\text{HH}_*^{\text{ch}}(\mathcal{H}) = \mathbb{C}[c] \otimes \Lambda(\sigma)\]
where $|c| = 2$ (central charge) and $|\sigma| = 1$ (desuspension of $S^1$).

The Connes operator $B: \text{HH}_n \to \text{HH}_{n+1}$ (degree $+1$) satisfies $B(c) = 0$,
$B(\sigma) = c$, giving:
\[\text{HC}_*^{\text{ch}}(\mathcal{H}) = \mathbb{C}[c]\]
(polynomials in the central charge).

\emph{Free fermion $\beta\gamma$ system.}
\[\text{HH}_*^{\text{ch}}(\beta\gamma) = \Lambda(\beta_0, \gamma_0) \otimes \mathbb{C}[c]\]
where $\beta_0, \gamma_0$ are zero modes. Cyclic homology adds periodicity:
\[\text{HC}_*^{\text{ch}}(\beta\gamma) = \mathbb{C}[c] \otimes
 \mathbb{C}[\beta_0^{-1}, \gamma_0^{-1}]_{\text{formal}}\]
(the localization $\mathbb{C}[\beta_0, \gamma_0][\beta_0^{-1}, \gamma_0^{-1}]$ at the zero-mode variables, completed formally).

The zero-mode periodicity in $\text{HC}_*^{\text{ch}}(\beta\gamma)$ reflects the symplectic pairing of the $\beta\gamma$ system: the localized zero modes span the deformation space of the Lagrangian splitting.
\end{computation}

\begin{remark}[Functoriality]
The chiral Hochschild-cyclic spectral sequence is functorial: a morphism
$f\colon \cA \to \mathcal{B}$ induces $f_*\colon E_r(\cA) \to E_r(\mathcal{B})$,
tensor products satisfy $E_r(\cA \otimes \mathcal{B}) \cong E_r(\cA) \otimes E_r(\mathcal{B})$
up to higher structure, and Koszul duality gives $E_r(\cA^!) \cong E_r(\cA)^\vee$.
The chiral Hochschild complex represents the functor
$\operatorname{Bimod}_{\cA} \ni M \mapsto \operatorname{Hom}_{\operatorname{Bimod}}(\operatorname{HH}(\cA), M)$.
\end{remark}

\subsection{Chiral Hochschild complex for chiral algebras}

\begin{definition}[Chiral Hochschild complex]
\label{def:chiral-hochschild}
\index{Hochschild cohomology!chiral|textbf}
For a chiral algebra $\mathcal{A}$ on a smooth curve $X$, the \emph{chiral Hochschild
complex} is:
\[\text{CH}_n(\mathcal{A}) = \Gamma\left(\overline{C}_{n+1}(X), 
 \mathcal{A}^{\boxtimes(n+1)} \otimes \det\left(\Omega^1_{\overline{C}_{n+1}(X)/X}\right)\right)\]

with differential:
\[d_{\text{HH}}(\omega) = \sum_{i=0}^{n} (-1)^i \left[\text{omit } i\text{-th factor}\right]\]

More explicitly, using the chiral product $\mu_{ij}$:
\begin{align*}
d_{\text{HH}}(a_0 \otimes \cdots \otimes a_n) 
&= \sum_{i=0}^{n-1} (-1)^i (a_0 \otimes \cdots \otimes \mu(a_i, a_{i+1}) 
 \otimes \cdots \otimes a_n) \\
&\quad + (-1)^n (\mu(a_n, a_0) \otimes a_1 \otimes \cdots \otimes a_{n-1})
\end{align*}

The last term implements the \emph{cyclic structure}: $a_n$ wraps around to multiply $a_0$.
\end{definition}

\begin{theorem}[Chiral Hochschild complex is a chain complex; \ClaimStatusProvedHere]
\label{thm:hochschild-chain-complex}
The identity $d_{\text{HH}}^2 = 0$ is the chiral Hochschild analogue of the Arnold-relation mechanism that ensured $d^2 = 0$ for the bar differential (\S\ref{sec:frame-bar-deg2}): adjacent face maps cancel in pairs. In the chiral setting, the same cancellation acquires OPE corrections from the higher poles.
The differential $d_{\text{HH}}$ satisfies $d_{\text{HH}}^2 = 0$, making
$(\text{CH}_*(\mathcal{A}), d_{\text{HH}})$ a chain complex.
\end{theorem}

\begin{proof}
We must show that for any $\omega \in \text{CH}_n(\mathcal{A})$:
\[d_{\text{HH}}^2(\omega) = 0\]

\emph{Step 1: Expand $d_{\text{HH}}^2$}

Applying $d_{\text{HH}}$ twice gives:
\begin{align*}
d_{\text{HH}}^2(a_0 \otimes \cdots \otimes a_n) 
&= d_{\text{HH}}\left(\sum_{i=0}^{n-1} (-1)^i (\cdots \otimes \mu(a_i, a_{i+1}) 
 \otimes \cdots)\right. \\
&\quad\left. + (-1)^n (\mu(a_n, a_0) \otimes a_1 \otimes \cdots)\right)
\end{align*}

\emph{Step 2: Identify canceling pairs}

After expanding, terms come in two types:
\begin{enumerate}
\item \emph{Type A}: Apply $\mu$ at positions $(i,i+1)$ then $(j,j+1)$ with $j \neq i, i+1$
\item \emph{Type B}: Apply $\mu$ twice at adjacent triples $(i,i+1,i+2)$
\end{enumerate}

\emph{Type A terms cancel} because applying $\mu$ at position~$i$ first reduces the chain length by~1, so the second application at position~$j$ (with $j > i+1$) picks up index $j-1$:
\[(-1)^i (-1)^{j-1} (\ldots) +
 (-1)^j (-1)^{i} (\ldots) = (-1)^{i+j-1} + (-1)^{i+j} = 0\]
(the index shift from the first contraction produces the sign difference)

\emph{Type B terms cancel} by the Borcherds identity (the chiral analog of associativity).
For three elements $a_i, a_{i+1}, a_{i+2}$ at pairwise distinct points $z_i, z_{i+1}, z_{i+2}$,
the Type~B contributions are:
\begin{align*}
&(-1)^i(-1)^{i+1}(\cdots \otimes \mu_{z_i, z_{i+2}}(\mu_{z_i, z_{i+1}}(a_i,a_{i+1}),a_{i+2}) \otimes \cdots) \\
&+ (-1)^{i+1}(-1)^i (\cdots \otimes \mu_{z_i, z_{i+2}}(a_i,\mu_{z_{i+1}, z_{i+2}}(a_{i+1},a_{i+2})) \otimes \cdots)
\end{align*}

The signs give $(-1)^{2i+1} = -1$ for the first and $(-1)^{2i+1} = -1$ for the second,
so the total contribution is:
\[-\bigl(\mu(\mu(a_i,a_{i+1}),a_{i+2}) - \mu(a_i,\mu(a_{i+1},a_{i+2}))\bigr)\]

By the Borcherds identity \cite[Section~3.4.7]{BD04}
(equivalently: the factorization algebra structure
encodes \emph{homotopy} associativity via the codimension-1 boundary strata
of $\overline{C}_3$), the iterated products
$\mu(\mu(a_i,a_{i+1}),a_{i+2})$ and $\mu(a_i,\mu(a_{i+1},a_{i+2}))$
agree up to the contribution of the boundary stratum $\partial \overline{C}_3$,
which is accounted for by the chiral Hochschild complex structure
(the face maps encode precisely these boundary identifications).
Thus the two terms cancel in the chiral Hochschild complex, giving $d_{\text{HH}}^2 = 0$.

\emph{Note}: Unlike the classical case, the chiral product is \emph{not} strictly associative;
the Borcherds identity provides associativity only up to total derivatives
(equivalently, up to homotopy). The cancellation above relies on the
factorization algebra axioms rather than strict associativity.
\end{proof}

\begin{definition}[Chiral Hochschild homology]
\label{def:chiral-HH}
The \emph{chiral Hochschild homology} of $\mathcal{A}$ is:
\[\text{HH}_n^{\text{ch}}(\mathcal{A}) = H_n(\text{CH}_*(\mathcal{A}), d_{\text{HH}})\]
\end{definition}

\subsection{\texorpdfstring{Cyclic structure and $S^1$-action}{Cyclic structure and S 1-action}}

\begin{definition}[Cyclic operator]
\label{def:cyclic-operator}
The \emph{cyclic operator} $t: \text{CH}_n(\mathcal{A}) \to \text{CH}_n(\mathcal{A})$ 
is defined by:
\[t(a_0 \otimes a_1 \otimes \cdots \otimes a_n) = (-1)^n (a_n \otimes a_0 \otimes a_1 
 \otimes \cdots \otimes a_{n-1})\]

This generates a $\mathbb{Z}/(n+1)$-action on $\text{CH}_n(\mathcal{A})$.
\end{definition}

\begin{lemma}[Cyclic operator commutes with the chiral Hochschild differential; \ClaimStatusProvedHere]
\label{lem:cyclic-commutes}
The cyclic operator commutes with the chiral Hochschild differential:
\[t \circ d_{\text{HH}} = d_{\text{HH}} \circ t\]
\end{lemma}

\begin{proof}
Direct computation using the definition of $d_{\text{HH}}$:
\begin{align*}
t(d_{\text{HH}}(a_0 \otimes \cdots \otimes a_n))
&= t\left(\sum_{i=0}^{n-1} (-1)^i (\cdots \otimes \mu(a_i,a_{i+1}) \otimes \cdots) 
 + (-1)^n (\mu(a_n,a_0) \otimes \cdots)\right)
\end{align*}

After applying $t$ (cyclic permutation), each term shifts indices: $i \to i+1 \pmod{n+1}$.

Similarly:
\[d_{\text{HH}}(t(a_0 \otimes \cdots \otimes a_n)) = 
 d_{\text{HH}}((-1)^n(a_n \otimes a_0 \otimes \cdots \otimes a_{n-1}))\]

After accounting for Koszul signs from moving $a_n$ past $a_0, \ldots, a_{n-1}$, 
the two expressions are identical.
\end{proof}

\begin{definition}[Connes operator B]
\label{def:connes-B}
\index{cyclic homology!Connes operator|textbf}
The \emph{Connes operator} $B: \mathrm{CH}_n(\mathcal{A}) \to \mathrm{CH}_{n+1}(\mathcal{A})$ is defined as
\[B = (1-t_{n+1}) \circ s \circ N_n\]
where $N_n = \sum_{i=0}^{n} t^i$ is the norm operator and $s: \mathrm{CH}_n \to \mathrm{CH}_{n+1}$ is the extra degeneracy $s(a_0 \otimes \cdots \otimes a_n) = 1 \otimes a_0 \otimes \cdots \otimes a_n$. The identities $B^2 = 0$ and $Bd + dB = 0$ hold (Theorem~\ref{thm:connes-exact-sequence}).
\end{definition}

\begin{theorem}[Connes mixed-complex structure {\cite{Connes85,Loday98}}; \ClaimStatusProvedElsewhere]
\label{thm:connes-exact-sequence}
The pair $(d_{\mathrm{HH}}, B)$ equips $\mathrm{CH}_*(\mathcal{A})$ with the
structure of a \emph{mixed complex}: $d^2 = B^2 = dB + Bd = 0$.
This gives rise to a short exact sequence of complexes:
\[0 \to \mathrm{CC}_*(\mathcal{A}) \to \mathrm{CC}_*^{\mathrm{per}}(\mathcal{A})
\to \mathrm{CC}_*^{\mathrm{neg}}(\mathcal{A})[2] \to 0\]
where:
\begin{itemize}
\item $\mathrm{CC}_* = \mathrm{CH}_* \otimes k[u]/(d + uB)$ is the cyclic complex
 ($|u| = -2$)
\item $\mathrm{CC}_*^{\mathrm{per}} = \mathrm{CH}_* \otimes k((u))/(d+uB)$ is the
 periodic cyclic complex
\item $\mathrm{CC}_*^{\mathrm{neg}}$ is the negative cyclic complex
\end{itemize}
\end{theorem}

\begin{remark}[Provenance and citation]
This theorem is imported and treated as \ClaimStatusProvedElsewhere. Standard
presentations of Connes' mixed-complex formalism and the associated exact
sequence are in \cite{Connes85,Loday98}.
\end{remark}

\begin{corollary}[Connes SBI exact sequence {\cite{Connes85,Loday98}}; \ClaimStatusProvedElsewhere]
\label{cor:connes-SBI}
There is a long exact sequence relating chiral Hochschild and cyclic homology:
\[\cdots \to \mathrm{HH}_n(\mathcal{A}) \xrightarrow{I} \mathrm{HC}_n(\mathcal{A}) \xrightarrow{S} \mathrm{HC}_{n-2}(\mathcal{A}) \xrightarrow{B} \mathrm{HH}_{n-1}(\mathcal{A}) \to \cdots\]
where $S$ is the periodicity operator, $B$ is Connes' operator, and $I$ is the natural inclusion. In particular, $S$ is an isomorphism in degrees where $\mathrm{HH}_*$ vanishes, yielding $2$-periodicity of periodic cyclic homology $\mathrm{HP}_* = \varprojlim_S \mathrm{HC}_{*+2k}$.
\end{corollary}

\subsection{The chiral Hochschild-cyclic spectral sequence}

\begin{theorem}[Chiral Hochschild-cyclic spectral sequence {\cite{Connes85,Loday98}}; \ClaimStatusProvedElsewhere]
\label{thm:HC-spectral-sequence}
\index{spectral sequence!Hochschild-cyclic}
The cyclic structure induces a spectral sequence:
\[E_1^{p,q} = \text{HH}_{q}^{\text{ch}}(\mathcal{A}) \otimes \Lambda^p(\mathbb{C} \cdot \sigma)\]
converging to:
\[E_\infty^{p,q} \Rightarrow \text{HC}_{p+q}^{\text{ch}}(\mathcal{A})\]

The $E_1$ differential is:
\[d_1: E_1^{p,q} \to E_1^{p-1,q}\]
\[d_1(\omega \otimes \sigma^p) = B(\omega) \otimes \sigma^{p-1}\]
where $B$ is Connes' operator.
\end{theorem}

\begin{remark}[Provenance and citation]
This theorem is imported and treated as \ClaimStatusProvedElsewhere. The
spectral sequence attached to the mixed complex $(\mathrm{CH}_*,d_{\mathrm{HH}},B)$
is standard in the cyclic-homology literature; see \cite{Connes85,Loday98}.
\end{remark}

\subsection{\texorpdfstring{$E_2$ page: explicit computation}{E2 page: explicit computation}}

\begin{theorem}[Second-page formula {\cite{Loday98}}; \ClaimStatusProvedElsewhere]
\label{thm:E2-page-formula}
The $E_2$ page of the chiral Hochschild-cyclic spectral sequence is:
\[E_2^{p,q} = \begin{cases}
\text{HH}_q(\mathcal{A})^{S^1} & \text{if } p = 0 \\
\text{HH}_{q-1}(\mathcal{A})_{S^1} & \text{if } p = 1 \\
0 & \text{if } p \geq 2
\end{cases}\]
where:
\begin{itemize}
\item $(-)^{S^1}$ denotes $S^1$-invariants (fixed points)
\item $(-)_{S^1}$ denotes $S^1$-coinvariants ($S^1$-orbits)
\end{itemize}
\end{theorem}

\begin{remark}[Provenance and citation]
This theorem is imported and treated as \ClaimStatusProvedElsewhere. The $E_2$
identification in terms of invariants/coinvariants of the circle action is the
standard computation for the cyclic spectral sequence (see \cite{Loday98}).
\end{remark}

\begin{example}[Second page for the Heisenberg algebra]
\label{ex:E2-heisenberg}
For the Heisenberg chiral algebra $\mathcal{H}$ at level $k$:

\emph{Step 1: Compute chiral Hochschild homology}
\[\text{HH}_*(\mathcal{H}) = \mathbb{C}[a_{-n}]_{n \geq 1} \otimes \mathbb{C} \cdot \mathbf{1}\]
where $a_{-n}$ are negative modes of the Heisenberg field $a(z) = \sum_n a_n z^{-n-1}$.

In more invariant terms:
\[\text{HH}_*(\mathcal{H}) = \text{Sym}^*(H_1(S^1, \mathbb{C})) \otimes \Lambda(H_0(S^1, \mathbb{C})) = \mathbb{C}[c] \otimes \Lambda(\sigma)\]
where $|c| = 2$ (from the $S^1$ homology) and $|\sigma| = 1$ (from the constant functions), consistent with the Serre duality computation.

\emph{Step 2: $S^1$-action}

The $S^1$-action on $\text{HH}_*(\mathcal{H})$ is trivial on the center, so:
\[\text{HH}_*(\mathcal{H})^{S^1} = \mathbb{C}[c]\]
\[\text{HH}_*(\mathcal{H})_{S^1} = \mathbb{C}[c]\]

\emph{Step 3: $E_2$ page}
\[E_2^{0,q} = \mathbb{C}[c] \cap \{|*| = q\} = \begin{cases}
\mathbb{C} & \text{if } q = 0, 2, 4, \ldots \\
0 & \text{otherwise}
\end{cases}\]

\[E_2^{1,q} = \mathbb{C}[c] \cap \{|*| = q-1\} = \begin{cases}
\mathbb{C} & \text{if } q = 1, 3, 5, \ldots \\
0 & \text{otherwise}
\end{cases}\]

The $E_2$ page is therefore:
\[E_2 = \begin{array}{c|cc}
q \backslash p & 0 & 1 \\
\hline
0 & \mathbb{C} & 0 \\
1 & 0 & \mathbb{C} \\
2 & \mathbb{C} & 0 \\
3 & 0 & \mathbb{C} \\
\vdots & \vdots & \vdots
\end{array}\]

The spectral sequence \emph{degenerates at $E_2$} (all higher differentials are zero)
because the only possible higher differentials $d_r: E_r^{1,q} \to E_r^{0,q+r}$ would require $r \geq 2$, but $E_r^{p,q} = 0$ for $p \geq 2$, so all higher differentials vanish.

\emph{Comparison with classical Hochschild cohomology.}
The polynomial $E_2$ page above should not be confused with the
ordinary classical Hochschild cohomology
$\mathrm{HH}^*(\mathcal{H})_{\mathrm{alg}}$, which is computed in
Example~\ref{ex:HH-heisenberg-complete}. The latter uses the Koszul
resolution (length~$2$) and gives
$\mathrm{HH}^n_{\mathrm{alg}}(\mathcal{H}) = \mathbb{C}$ for
$n = 0, 1, 2$ and
$\mathrm{HH}^n_{\mathrm{alg}}(\mathcal{H}) = 0$ for $n \geq 3$.
The difference is that the $E_2$ page here is computed from chiral
Hochschild \emph{homology}
$\mathrm{HH}^{\mathrm{ch}}_*(\mathcal{H})
= \mathbb{C}[c] \otimes \Lambda(\sigma)$, which is polynomial and
does not vanish in high degrees. Classical Hochschild cohomology
\textup{(}the $\mathrm{Ext}$-computation\textup{)} and chiral
Hochschild homology \textup{(}the $\mathrm{Tor}$-computation\textup{)}
are distinct invariants; the former detects deformations, while the
latter feeds the cyclic spectral sequence.
\end{example}

\begin{example}[Second page for affine sl3]
\label{ex:E2-sl3}
\index{$\mathfrak{sl}_3$!Hochschild-cyclic spectral sequence}
For $\widehat{\mathfrak{sl}}_3$ at generic level~$k$:

\emph{Step~1: Chiral Hochschild homology.}
By the continuous cohomology of current algebras, $\mathrm{HH}_*^{\mathrm{ch}}(\widehat{\mathfrak{sl}}_3)$ is determined by the Lie algebra cohomology $H^*(\mathfrak{sl}_3; \mathbb{C}) = \Lambda(x_3, x_5)$ (exterior algebra on generators of degrees $3$ and $5$, corresponding to the exponents $m_1 = 1$, $m_2 = 2$ of $\mathfrak{sl}_3$) tensored with the polynomial algebra from the loop direction. This gives:
\[\mathrm{HH}_*^{\mathrm{ch}}(\widehat{\mathfrak{sl}}_3)
= \mathbb{C}[\Theta_2, \Theta_3] \otimes \Lambda(\sigma_3, \sigma_5)\]
where $|\Theta_j| = j$ (from the Casimir operators of degrees $2$ and $3$, corresponding to the exponents $m_1 = 1$, $m_2 = 2$) and $|\sigma_{2i+1}| = 2i+1$ (from $H^*(\mathfrak{sl}_3)$).

\emph{Step~2: $S^1$-action and $E_2$ page.}
The $S^1$-action on the polynomial part is trivial (Casimirs are invariant).
The exterior generators $\sigma_3, \sigma_5$ lie in odd degrees and are
$S^1$-coinvariants:
\[E_2^{0,*} = \mathbb{C}[\Theta_2, \Theta_3], \qquad
E_2^{1,*} = \mathbb{C}[\Theta_2, \Theta_3].\]

\emph{Step~3: Degeneration.}
At generic~$k$, $\widehat{\mathfrak{sl}}_3$ is simple (Ext-vanishing in
category~$\mathcal{O}$), so the spectral sequence degenerates at~$E_2$ by
the same argument as for $\widehat{\mathfrak{sl}}_2$. The Hilbert function
of $\mathrm{HC}_n = E_2^{0,n} \oplus E_2^{1,n-1}$ gives:
\[\dim \mathrm{HC}_n^{\mathrm{ch}}(\widehat{\mathfrak{sl}}_3)
= \#\{(a,b) : 2a + 3b = n\} + \#\{(a,b) : 2a + 3b = n-1\}\]
which grows linearly in~$n$ (rank~$2$), in contrast to the constant
$\dim \mathrm{HC}_n = 1$ for $\widehat{\mathfrak{sl}}_2$ (rank~$1$).
\end{example}

\begin{example}[Second page for lattice VOAs]
\label{ex:E2-lattice}
\index{lattice vertex algebra!Hochschild-cyclic}
For a lattice VOA $V_\Lambda$ of rank~$d$, the underlying Heisenberg
algebra $\mathcal{H}^{\otimes d}$ gives:
\[\mathrm{HH}_*^{\mathrm{ch}}(V_\Lambda) = \mathbb{C}[c_1, \ldots, c_d]
\otimes \Lambda(\sigma_1, \ldots, \sigma_d)\]
with $|c_i| = 2$, $|\sigma_i| = 1$. The lattice vertex operators do not
contribute additional chiral Hochschild classes (they are inner automorphisms of the
Heisenberg algebra at generic level). Thus
$E_2^{0,*} = \mathbb{C}[c_1, \ldots, c_d]$
and $E_2^{1,*} = \mathbb{C}[c_1, \ldots, c_d]$, with
$E_2$ degeneration.
\end{example}

\subsection{Physical interpretation: anomalies and partition functions}

\begin{theorem}[Partition function as cyclic homology {\cite{FT87,BZFN10}}; \ClaimStatusProvedElsewhere]
\label{thm:partition-cyclic}
For a 2d CFT with chiral algebra $\mathcal{A}$ on a genus $g$ surface $\Sigma_g$,
the partition function is:
\[Z[\Sigma_g] = \int_{\Sigma_g} \mathcal{A} = \mathrm{Tr}_{\mathrm{HC}_*(\mathcal{A})}(q^{L_0})\]

The chiral Hochschild-cyclic spectral sequence computes $Z[\Sigma_g]$ with:
\begin{itemize}
\item $E_1$ = tree-level (genus 0 contribution)
\item $E_2$ = one-loop (genus 1 + quantum corrections)
\item $E_r$ ($r \geq 3$) = multi-loop corrections (genus $\geq 2$)
\end{itemize}
\end{theorem}

\begin{remark}[Provenance]
The identification of the partition function with cyclic homology is due to Feigin--Tsygan \cite{FT87}: the factorization homology $\int_{\Sigma_g} \mathcal{A}$ is computed by the cyclic complex $\mathrm{HC}_*(\mathcal{A})$ via the identification of the free loop space $LX$ with the cyclic bar construction. For chiral algebras specifically, the result follows from the equivalence between factorization homology on a closed surface and the trace over the category of modules, established by Ben-Zvi--Francis--Nadler \cite{BZFN10}.
\end{remark}

\subsection{Master computation table}

\begin{table}[H]
\centering
\caption{\texorpdfstring{$E_2$}{E2} page computation for standard examples}
\begin{tabular}{|l|c|c|c|}
\hline
\textbf{Chiral Algebra} & $\mathbf{E_2^{0,*}}$ & $\mathbf{E_2^{1,*}}$ &
\emph{Degeneration?} \\
\hline
Heisenberg $\mathcal{H}_k$ & $\mathbb{C}[c]$ (even deg) & $\mathbb{C}[c]$ (odd deg) &
Yes (at $E_2$) \\
\hline
$\beta\gamma$ bosons & $\mathbb{C}[c](1 \oplus \beta_0\gamma_0)$ & $\mathbb{C}[c]$ &
Yes (at $E_2$) \\
\hline
$bc$ ghosts & Similar to $\beta\gamma$ & Similar to $\beta\gamma$ & Yes (at $E_2$) \\
\hline
Virasoro $\mathcal{V}_c$ (generic $c$) & $\mathbb{C}[\Theta]$ ($|\Theta| = 2$) & 0 &
Yes (at $E_2$, generic $c$)${}^\dagger$ \\
\hline
$\widehat{\mathfrak{sl}}_2$ level $k$ & $\mathbb{C}[c]$ & $\mathbb{C}[c]$ & Yes (at $E_2$) \\
\hline
$\widehat{\mathfrak{sl}}_3$ level $k$ & $\mathbb{C}[\Theta_2, \Theta_3]$ & $\mathbb{C}[\Theta_2, \Theta_3]$ & Yes (at $E_2$, generic $k$) \\
\hline
$W_3$ algebra & $\mathbb{C}[\Theta_2, \Theta_3]$ & $\mathbb{C}[\Theta_2]$ & Depends on $c$ \\
\hline
$W_N$ algebra ($N \geq 4$) & $\mathbb{C}[\Theta_2, \ldots, \Theta_N]$ & $\mathbb{C}[\Theta_2, \ldots, \Theta_{N-1}]$ & Yes (generic $c$) \\
\hline
Lattice $V_\Lambda$ (rank $d$) & $\mathbb{C}[c]^{\otimes d}$ & $\mathbb{C}[c]^{\otimes d}$ & Yes (at $E_2$) \\
\hline
$Y(\mathfrak{sl}_2)^{\mathrm{ch}}$ & $\mathbb{C}[\Theta_2]$ & $\mathbb{C}$ & Conjectural \\
\hline
\end{tabular}

\smallskip\noindent
${}^\dagger$\,The $E_2^{0,*}$ column records chiral Hochschild \emph{homology}
$\mathrm{HH}_*^{\mathrm{ch}}(\cA)^{S^1}$ (the Tor computation), which
is polynomial for the Virasoro. This is distinct from chiral Hochschild
\emph{cohomology} $\ChirHoch^*(\cA)$ (the Ext computation), which is
of cohomological amplitude~$[0,2]$ by Theorem~H
(Theorem~\ref{thm:hochschild-polynomial-growth}). The two invariants
coincide in degree~$0$ ($\mathrm{HH}_0 \cong \ChirHoch^0 = Z(\cA)$)
but diverge in higher degrees.
\end{table}

\subsection{Cyclic homology exchange under Koszul duality}

\begin{corollary}[Cyclic homology duality; \ClaimStatusProvedHere]\label{cor:cyclic-homology-duality}
\index{cyclic homology!Koszul duality}
For a Koszul pair $(\mathcal{A}, \mathcal{A}^!)$, the Connes periodicity operator\index{Connes periodicity operator} $S$ intertwines the Koszul duality on chiral Hochschild homology with a $[-2]$-shifted duality on cyclic homology:
\begin{equation}\label{eq:cyclic-duality}
\mathrm{HC}_n(\mathcal{A}) \;\cong\; \mathrm{HC}_{-n}(\mathcal{A}^!)^{\vee}
\end{equation}
for all $n$, where $\mathrm{HC}_*$ denotes periodic cyclic homology.
\end{corollary}

\begin{proof}
The SBI exact sequence (Corollary~\ref{cor:connes-SBI}) relates $\mathrm{HH}_*$ and $\mathrm{HC}_*$ via the periodicity operator $S$. The Koszul duality for chiral Hochschild cohomology (Theorem~\ref{thm:main-koszul-hoch}) gives $\mathrm{HH}^n(\mathcal{A}) \cong \mathrm{HH}^{2-n}(\mathcal{A}^!)^\vee \otimes \omega_X$. Inserting this into the SBI sequence for $\mathcal{A}$ and comparing with the SBI sequence for $\mathcal{A}^!$: the periodicity operator $S$ shifts degree by $-2$ on both sides, so the duality on $\mathrm{HH}_*$ descends to periodic cyclic homology as stated. The shift by~$2$ in the chiral Hochschild duality is absorbed by the periodicity $S$, yielding the unshifted duality~\eqref{eq:cyclic-duality} on $\mathrm{HP}_* = \varprojlim_S \mathrm{HC}_{*+2k}$.
\end{proof}

\begin{remark}\label{rem:cyclic-koszul-virasoro}
For the Virasoro algebra $\mathrm{Vir}_c$ and its same-family partner
$\mathrm{Vir}_{26-c}$: both have $\ChirHoch^*$ concentrated in
$\{0, 2\}$ with $\ChirHoch^0 = \ChirHoch^2 = \mathbb{C}$
(Theorem~\ref{thm:virasoro-hochschild}). The deformation class
$\Theta \in \ChirHoch^2(\mathrm{Vir}_c)$ and its dual
$\Theta' \in \ChirHoch^2(\mathrm{Vir}_{26-c})$ are exchanged by
the Koszul duality (Theorem~\ref{thm:main-koszul-hoch}),
consistent with the Verdier anti-commutativity of the Kodaira--Spencer
class (Theorem~\ref{thm:kodaira-spencer-chiral-complete}). The partner
$\mathrm{Vir}_{26-c}$ is the same-family Koszul dual
(Theorem~\ref{thm:modular-characteristic}); the infinite-generator
realization via the $W_\infty$ completion programme is treated in
Chapter~\ref{chap:concordance}.
\end{remark}

\begin{corollary}[Chiral Hochschild cup product exchange; \ClaimStatusProvedHere]
\label{cor:hochschild-cup-exchange}
\index{Hochschild cohomology!cup product exchange}
For a Koszul pair $(\mathcal{A}, \mathcal{A}^!)$, let $\Theta \in CH^2(\mathcal{A})$ be a periodicity class \textup{(}as in Theorem~\textup{\ref{thm:virasoro-periodicity})}. Under the Koszul duality isomorphism $CH^n(\mathcal{A}) \cong CH^{2-n}(\mathcal{A}^!)^\vee \otimes \omega_X$ \textup{(}Theorem~\textup{\ref{thm:main-koszul-hoch})}, the cup product with $\Theta$ corresponds to the cup product with the dual class $\Theta' \in CH^2(\mathcal{A}^!)$ up to sign:
\begin{equation}\label{eq:cup-product-exchange}
\Theta \;\longleftrightarrow\; -\Theta'
\end{equation}
under the Verdier anti-commutativity of the Kodaira--Spencer class.
\end{corollary}

\begin{proof}
The Kodaira--Spencer class $\mathrm{KS}_g(\mathcal{A}) \in H^1(\overline{\mathcal{M}}_g, Z(\mathcal{A}))$ satisfies $\mathrm{KS}_g(\mathcal{A}) = -\mathrm{KS}_g(\mathcal{A}^!)$ under the Verdier involution (Theorem~\ref{thm:kodaira-spencer-chiral-complete}, equation~\eqref{eq:verdier-ks-anticommute}). The periodicity class $\Theta$ arises from the $g = 0$ contribution to the Kodaira--Spencer class via the bar complex on $\overline{\mathcal{M}}_{0,4} \cong \mathbb{P}^1$ (proof of Theorem~\ref{thm:virasoro-periodicity}, Step~1). The Verdier anti-commutativity descends to the periodicity generators: $\Theta$ on the $\mathcal{A}$ side corresponds to $-\Theta'$ on the $\mathcal{A}^!$ side.
\end{proof}

\begin{remark}[Virasoro verification]\label{rem:cup-exchange-virasoro}
For $\mathrm{Vir}_c$ with $\ChirHoch^2 = \mathbb{C}\cdot\Theta$ and its
same-family partner $\mathrm{Vir}_{26-c}$ with $\ChirHoch^2 =
\mathbb{C}\cdot\Theta'$: the Koszul duality isomorphism
$\ChirHoch^2(\mathrm{Vir}_c) \cong \ChirHoch^0(\mathrm{Vir}_{26-c})^\vee
\otimes \omega_X$ maps $\Theta \mapsto -\Theta'$ (up to the
$\omega_X$ twist), where the sign comes from the Verdier
anti-commutativity $\Theta \leftrightarrow -\Theta'$. This is
consistent with the periodic cyclic duality
(Corollary~\ref{cor:cyclic-homology-duality}).
\end{remark}

\section{Derived center and topological Hochschild cochains (M4)}
\label{sec:derived-center-hochschild-cochains}

\index{derived center|textbf}
\index{Morita equivalence!Hochschild cohomology}
\index{compact generator|textbf}

The derived center of a dg-category is the derived endomorphisms of
the identity functor. For a category with a compact generator, this
reduces, via the Morita equivalence, to the topological Hochschild cochain
complex of the endomorphism algebra. The argument is categorical in
nature and depends on three classical inputs: Morita theory for
dg-categories, the identification of endofunctors with bimodules, and
the definition of topological Hochschild cochains as bimodule self-Ext.
The topological Hochschild cohomology in this section is the classical
(topological) $\mathrm{HH}^\bullet(A,A) = \RHom_{A^e}(A,A)$ of
associative dg-algebras; the chiral upgrade to $\ChirHoch^*$
incorporating OPE data and curve geometry is developed in the
earlier sections of this chapter.

\subsection{Compact generators and the Morita equivalence}

\begin{definition}[Compact generator]\label{def:compact-generator}
Let $\mathcal{C}$ be a $k$-linear dg-category admitting all cones,
shifts, and retracts (i.e.\ a pretriangulated dg-category). An
object $b \in \mathcal{C}$ is a \emph{compact generator} if:
\begin{enumerate}[label=(\roman*)]
\item \emph{Compactness}: the functor
 $\RHom_{\mathcal{C}}(b, -)\colon \mathcal{C} \to \Ch(k)$
 preserves arbitrary coproducts (equivalently, filtered colimits);
\item \emph{Generation}: if $\RHom_{\mathcal{C}}(b, c) \simeq 0$
 for an object $c \in \mathcal{C}$, then $c \simeq 0$.
\end{enumerate}
Write $A := \RHom_{\mathcal{C}}(b, b)$ for the endomorphism
dg-algebra.
\end{definition}

\begin{proposition}[Morita equivalence {\cite{Keller06,Toen07}}; \ClaimStatusProvedElsewhere]
\label{prop:morita-equivalence-compact-gen}
\index{Morita equivalence|textbf}
Let $\mathcal{C}$ be a pretriangulated dg-category and
$b \in \mathcal{C}$ a compact generator with
$A = \RHom_{\mathcal{C}}(b, b)$. Define the functor
\[
\Psi\colon \mathcal{C} \;\longrightarrow\;
\mathrm{Perf}(A), \qquad
\Psi(c) := \RHom_{\mathcal{C}}(b, c),
\]
where $\mathrm{Perf}(A)$ denotes the dg-category of perfect
\textup{(}compact\textup{)} right $A$-modules. Then $\Psi$ is a
quasi-equivalence of dg-categories.
\end{proposition}

\begin{proof}
The argument has two steps.

\emph{Fully faithful.}
For any $c, c' \in \mathcal{C}$, the map
\[
\Psi_{c,c'}\colon \RHom_{\mathcal{C}}(c, c')
\;\longrightarrow\;
\RHom_A(\RHom_{\mathcal{C}}(b,c),\, \RHom_{\mathcal{C}}(b,c'))
\]
is the composition map. When $c = b$, the right-hand side is
$\RHom_A(A, \Psi(c')) \simeq \Psi(c')$, which equals the left-hand
side $\RHom_{\mathcal{C}}(b, c')$ by definition. The full
subcategory of objects $c$ for which $\Psi_{c,-}$ is an isomorphism
contains~$b$ and is closed under cones, shifts, and retracts (since
$\RHom_{\mathcal{C}}(-, c')$ and $\Psi$ both preserve these
operations). Since $b$ generates~$\mathcal{C}$, the subcategory
is all of~$\mathcal{C}$.

\emph{Essentially surjective.}
The image of $\Psi$ contains the free module
$A = \Psi(b)$ and is closed under cones, shifts, and retracts (since
$\Psi$ is an exact functor of pretriangulated categories). Every
perfect $A$-module is built from $A$ by finitely many cones, shifts,
and retracts, so $\Psi$ is essentially surjective onto
$\mathrm{Perf}(A)$.

The result is standard: see Keller~\cite{Keller06},
Schwede--Shipley~\cite{SS03},
and To\"en~\cite{Toen07} for the $\infty$-categorical refinement.
\end{proof}

\subsection{The derived center}

\begin{definition}[Derived center of a dg-category]
\label{def:derived-center}
\index{derived center|textbf}
For a $k$-linear dg-category $\mathcal{C}$, the \emph{derived center}
is the dg-algebra of derived endomorphisms of the identity functor:
\[
Z_{\mathrm{der}}(\mathcal{C})
:= \RHom_{\mathrm{Fun}(\mathcal{C}, \mathcal{C})}
 (\mathrm{Id}_{\mathcal{C}},\, \mathrm{Id}_{\mathcal{C}}).
\]
A degree-$n$ cocycle in $Z_{\mathrm{der}}(\mathcal{C})$ is a
natural transformation $\mathrm{Id}_{\mathcal{C}} \Rightarrow
\mathrm{Id}_{\mathcal{C}}[n]$; its cohomology class is a derived
natural transformation. The product on $Z_{\mathrm{der}}(\mathcal{C})$
is composition of natural transformations; in particular,
$H^0(Z_{\mathrm{der}}(\mathcal{C}))$ is the ordinary center of the
homotopy category $[\mathcal{C}]$.
\end{definition}

\subsection{Endofunctors as bimodules}

The bridge between the derived center and topological Hochschild cochains is the
identification of endofunctors with bimodules.

\begin{proposition}[Endofunctor--bimodule equivalence {\cite{Toen07,BZFN10}};
\ClaimStatusProvedElsewhere]
\label{prop:endofunctor-bimodule}
\index{bimodule!endofunctor equivalence}
For a dg-algebra~$A$, there is a quasi-equivalence of dg-categories
\[
\mathrm{Fun}_{\mathrm{cocont}}(\mathrm{Perf}(A),\,
\mathrm{Perf}(A))
\;\simeq\; A\text{-}\mathrm{bimod}^{\mathrm{perf}},
\]
where the left-hand side consists of cocontinuous \textup{(}colimit-preserving\textup{)} dg-functors
$\mathrm{Perf}(A) \to \mathrm{Perf}(A)$, and the right-hand side
is the dg-category of perfect $A$-$A$-bimodules
\textup{(}equivalently, perfect $A^e$-modules, where
$A^e = A \otimes A^{\mathrm{op}}$\textup{)}. The equivalence sends
a bimodule $M$ to the tensor functor $- \otimes_A^{\mathbf{L}} M$.
\end{proposition}

\begin{proof}[Proof sketch]
The Eilenberg--Watts theorem for dg-categories: every cocontinuous
functor $F\colon \mathrm{Perf}(A) \to \mathrm{Perf}(A)$ is
represented by the bimodule $M_F := F(A)$, where $A$ carries its
canonical left module structure and $M_F$ inherits a right
$A$-structure from the right action of $A = \End(A)$ on the free
module. The assignment $F \mapsto F(A)$ is quasi-inverse to
$M \mapsto (- \otimes_A^{\mathbf{L}} M)$. See
To\"en~\cite{Toen07} and Ben-Zvi--Francis--Nadler~\cite{BZFN10}
for the $\infty$-categorical statement.
\end{proof}

\begin{corollary}[Identity functor $=$ diagonal bimodule]
\label{cor:identity-diagonal}
Under the equivalence of
Proposition~\textup{\ref{prop:endofunctor-bimodule}}, the identity
functor $\mathrm{Id}\colon \mathrm{Perf}(A) \to \mathrm{Perf}(A)$
corresponds to the diagonal bimodule ${}_A A_A$.
\end{corollary}

\begin{proof}
The identity functor sends the free module~$A$ to itself:
$\mathrm{Id}(A) = A$. The corresponding bimodule is therefore~$A$,
with left $A$-action by left multiplication and right $A$-action by
right multiplication. This is the diagonal bimodule.
\end{proof}

\subsection{The main identification}

\begin{theorem}[Derived center $=$ topological Hochschild cochains;
\ClaimStatusProvedHere]
\label{thm:derived-center-hochschild}
\index{derived center!Hochschild identification}
\index{Hochschild cohomology!derived center}
Let\/ $\mathcal{C}$ be a pretriangulated dg-category with compact
generator $b$, and set $A = \RHom_{\mathcal{C}}(b, b)$. There is a
natural quasi-isomorphism of dg-algebras
\begin{equation}\label{eq:derived-center-HH}
Z_{\mathrm{der}}(\mathcal{C})
\;\simeq\;
\mathrm{HH}^\bullet(A, A)
:= \RHom_{A^e}(A, A).
\end{equation}
In particular, the derived center depends on $\mathcal{C}$ only up to
Morita equivalence.
\end{theorem}

\begin{proof}
The proof assembles the three preceding results.

\emph{Step~1} (Morita reduction).
By Proposition~\ref{prop:morita-equivalence-compact-gen}, $b$ being a
compact generator gives a quasi-equivalence
$\Psi\colon \mathcal{C} \xrightarrow{\;\sim\;} \mathrm{Perf}(A)$.
The derived center is manifestly invariant under quasi-equivalence of
dg-categories (a quasi-equivalence $\Psi$ induces a quasi-isomorphism
$\Psi_*\colon Z_{\mathrm{der}}(\mathcal{C})
\xrightarrow{\sim} Z_{\mathrm{der}}(\mathrm{Perf}(A))$
by conjugation: $\alpha \mapsto \Psi \circ \alpha \circ \Psi^{-1}$),
so
\[
Z_{\mathrm{der}}(\mathcal{C})
\;\simeq\;
Z_{\mathrm{der}}(\mathrm{Perf}(A))
= \RHom_{\mathrm{Fun}(\mathrm{Perf}(A), \mathrm{Perf}(A))}
 (\mathrm{Id},\, \mathrm{Id}).
\]

\emph{Step~2} (Endofunctors $=$ bimodules).
By Proposition~\ref{prop:endofunctor-bimodule}, cocontinuous
endofunctors of $\mathrm{Perf}(A)$ are identified with
$A$-bimodules. Applying $\RHom$ in the functor category translates
to $\RHom$ in the bimodule category:
\[
\RHom_{\mathrm{Fun}}(\mathrm{Id},\, \mathrm{Id})
\;\simeq\;
\RHom_{A\text{-}\mathrm{bimod}}
 (M_{\mathrm{Id}},\, M_{\mathrm{Id}}).
\]

\emph{Step~3} (Identity $\mapsto$ diagonal).
By Corollary~\ref{cor:identity-diagonal}, $M_{\mathrm{Id}} = {}_A A_A$
is the diagonal bimodule. Therefore:
\[
Z_{\mathrm{der}}(\mathrm{Perf}(A))
\;\simeq\;
\RHom_{A^e}(A, A)
= \mathrm{HH}^\bullet(A, A).
\]

\emph{Naturality.} Each step is natural: the Morita equivalence is
natural in the generator~$b$, the endofunctor--bimodule equivalence is
natural in~$A$, and $\RHom$ is a bifunctor. The composite
isomorphism~\eqref{eq:derived-center-HH} is therefore natural
in~$\mathcal{C}$.
\end{proof}

\begin{remark}[Provenance]
\label{rem:derived-center-provenance}
The identification $Z_{\mathrm{der}}(\mathcal{C}) \simeq
\mathrm{HH}^\bullet(A)$ is implicit in Keller~\cite{Keller06} and
made explicit in the framework of $(\infty,1)$-categories by
Ben-Zvi--Francis--Nadler~\cite{BZFN10} and
To\"en~\cite{Toen07}. The argument presented here distills the
essential chain of identifications without passing through the full
$(\infty,2)$-categorical machinery. For the factorization-algebra
refinement relevant to chiral algebras, see
Costello--Gwilliam~\cite[Chapter~5]{CG17}.
\end{remark}

\subsection{Independence of generator: Morita invariance of
topological Hochschild cohomology}

\begin{theorem}[Morita invariance of $\mathrm{HH}^\bullet$;
\ClaimStatusProvedHere]
\label{thm:morita-invariance-HH}
\index{Hochschild cohomology!Morita invariance|textbf}
\index{Morita equivalence!Hochschild invariance}
Let $A$ and $A'$ be dg-algebras that are Morita equivalent, meaning
there exists a dg-category $\mathcal{C}$ with compact generators
$b, b'$ such that $A \simeq \RHom(b,b)$ and
$A' \simeq \RHom(b',b')$. Then there is a natural quasi-isomorphism
\[
\mathrm{HH}^\bullet(A, A) \;\simeq\; \mathrm{HH}^\bullet(A', A').
\]
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:derived-center-hochschild}, both sides are
quasi-isomorphic to $Z_{\mathrm{der}}(\mathcal{C})$, which depends
only on the dg-category~$\mathcal{C}$ and not on the choice of
generator. Concretely, the chain of quasi-isomorphisms is:
\[
\mathrm{HH}^\bullet(A)
\xleftarrow{\;\sim\;}
Z_{\mathrm{der}}(\mathcal{C})
\xrightarrow{\;\sim\;}
\mathrm{HH}^\bullet(A').
\]
\end{proof}

For the explicit bimodule construction of the Morita transfer map, we
record the following refinement.

\begin{proposition}[Explicit Morita transfer; \ClaimStatusProvedHere]
\label{prop:explicit-morita-transfer}
\index{Morita equivalence!explicit transfer map}
Let $P = \RHom_{\mathcal{C}}(b, b')$ and
$P^\vee = \RHom_{\mathcal{C}}(b', b)$ be the bimodules implementing
the Morita equivalence, so that
$P \otimes_{A'}^{\mathbf{L}} P^\vee \simeq A$ and
$P^\vee \otimes_A^{\mathbf{L}} P \simeq A'$. The Morita transfer
map
\begin{equation}\label{eq:morita-transfer-map}
\Phi\colon \mathrm{HH}^\bullet(A)
\;\longrightarrow\; \mathrm{HH}^\bullet(A'),
\qquad
f \;\longmapsto\;
P^\vee \otimes_A^{\mathbf{L}} f \otimes_A^{\mathbf{L}} P,
\end{equation}
is a quasi-isomorphism of dg-algebras.
\end{proposition}

\begin{proof}
We verify $\Phi$ is well-defined, multiplicative, and a
quasi-isomorphism.

\emph{Well-definedness.}
An element $f \in \mathrm{HH}^n(A) = \RHom_{A^e}(A, A)^n$
is an $A$-bimodule map $A \to A[n]$. The conjugation
$\Phi(f) := P^\vee \otimes_A f \otimes_A P$ is the composition
\[
A' \simeq P^\vee \otimes_A P
\xrightarrow{\mathrm{id} \otimes f \otimes \mathrm{id}}
P^\vee \otimes_A A[n] \otimes_A P
\simeq P^\vee \otimes_A P[n]
\simeq A'[n],
\]
which uses $A \otimes_A P \simeq P$ and
$P^\vee \otimes_A A \simeq P^\vee$ (left/right unit). The
composite is an $A'$-bimodule map $A' \to A'[n]$, hence an element
of $\mathrm{HH}^n(A')$.

\emph{Multiplicativity.}
For $f, g \in \mathrm{HH}^\bullet(A)$, the composition
$\Phi(f) \circ \Phi(g)$ is
$P^\vee \otimes_A f \otimes_A P \circ P^\vee \otimes_A g \otimes_A P$.
Using $P \otimes_{A'} P^\vee \simeq A$ to contract the inner
$P$-$P^\vee$ pair:
\[
\Phi(f) \circ \Phi(g)
= P^\vee \otimes_A f \otimes_A \underbrace{(P \otimes_{A'} P^\vee)}_{\simeq A}
 \otimes_A g \otimes_A P
\simeq P^\vee \otimes_A (f \circ g) \otimes_A P
= \Phi(f \circ g).
\]

\emph{Quasi-isomorphism.}
The inverse map $\Phi^{-1}(g) = P \otimes_{A'} g \otimes_{A'} P^\vee$
is constructed symmetrically. Since
$P \otimes_{A'} P^\vee \simeq A$ and
$P^\vee \otimes_A P \simeq A'$, we have
$\Phi^{-1} \circ \Phi \simeq \mathrm{id}$ and
$\Phi \circ \Phi^{-1} \simeq \mathrm{id}$, using the same
contraction. Hence $\Phi$ is a quasi-isomorphism.
\end{proof}

\begin{remark}[Chiral application]\label{rem:derived-center-chiral}
\index{derived center!chiral application}
For a chiral algebra $\cA$ on a curve~$X$, the module category
$\mathrm{Mod}_\cA$ (Definition~\ref{def:module-categories}) is a
pretriangulated dg-category. When $\mathrm{Mod}_\cA$ is compactly
generated with compact generator $\mathrm{Free}_\cA(k)$,
Theorem~\ref{thm:derived-center-hochschild} gives
\[
Z_{\mathrm{der}}(\mathrm{Mod}_\cA)
\;\simeq\;
\ChirHoch^\bullet(\cA, \cA).
\]
This identification controls the deformations of the
\emph{category} $\mathrm{Mod}_\cA$, not merely the algebra~$\cA$
itself: an element of $\ChirHoch^2(\cA)$ deforms the identity functor
on modules, hence the entire module theory.

\emph{Compact generation for the standard families.}
The hypothesis is verified in the following cases:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Heisenberg $\mathcal{H}_k$} ($k \neq 0$):
 the module category is equivalent to $\mathrm{Mod}_{\mathrm{Weyl}}$
 (Weyl algebra modules), which is compactly generated by the
 vacuum module~$F_0$. (The Weyl algebra is Morita-simple.)
\item \emph{Universal affine $V_k(\fg)$} at generic~$k$:
 the category $\mathrm{KL}_k(\fg)$ (Kazhdan--Lusztig category) is
 compactly generated by generalized Verma modules~\cite{KL93}.
 At non-generic (e.g., admissible)
 levels, compact generation holds by the Arakawa--Kawasetsu
 theorem~\cite{AK18} ($C_2$-cofiniteness for the simple quotient
 $L_k(\fg)$).
\item \emph{Virasoro $\mathrm{Vir}_c$} at generic~$c$:
 the free-field resolution (Feigin--Fuchs) provides a
 compact generator. At rational~$c$, compact generation
 follows from $C_2$-cofiniteness of the minimal model
 $L(c_{p,q}, 0)$~\cite{Miyamoto04}.
\item \emph{Principal $\mathcal{W}$-algebras}: compact generation
 follows from the quantum Drinfeld--Sokolov reduction, which
 preserves compact generation when the BRST complex is
 well-defined~\cite{Arakawa15}.
\end{enumerate}
For the universal algebras at generic level (the primary setting
of this monograph), compact generation is unconditional.
The hypothesis fails only for pathological algebras with
uncountably-generated module categories, which do not arise in
the Lie-theoretic landscape.
\end{remark}

\section{Factorization homology on the annulus: topological Hochschild chains (M7)}
\label{sec:annulus-hochschild-chains}

\index{factorization homology!annulus|textbf}
\index{topological Hochschild homology!excision|textbf}
\index{excision!factorization homology|textbf}

The complementary side of topological Hochschild theory is homological: while
topological Hochschild cochains are the derived center (deformations of the
identity functor), topological Hochschild chains are the derived trace
(factorization homology over the circle). The excision axiom for
factorization homology reduces the circle computation to a tensor
product over an interval, yielding the identification of factorization
homology on $S^1$ with topological Hochschild chains.

\subsection{Factorization homology: recollections}

\begin{definition}[Factorization homology over a manifold]
\label{def:factorization-homology-manifold}
\index{factorization homology|textbf}
For a locally constant factorization algebra $\mathcal{F}$ on a
manifold~$M$ with values in a symmetric monoidal
$\infty$-category~$\mathcal{V}$, the \emph{factorization homology}
of $\mathcal{F}$ over~$M$ is the global sections:
\[
\int_M \mathcal{F}
:= \mathcal{F}(M)
\;\in\; \mathcal{V}.
\]
When $\mathcal{F}$ is constructible rather than locally constant,
this is the homotopy colimit of $\mathcal{F}$ over the
Weiss topology on~$M$
\textup{(}Ayala--Francis~\cite{AF15},
Costello--Gwilliam~\cite{CG17}\textup{)}.
\end{definition}

The factorization homology functor satisfies two fundamental
properties that make it computable: \emph{local constancy} (the
value on a disk is determined by the $\En$-algebra structure) and
\emph{excision} (the value on a glued manifold is computed by a
derived tensor product).

\begin{theorem}[Excision; {\cite[Theorem~3.18]{AF15}}; \ClaimStatusProvedElsewhere]
\label{thm:excision}
\index{excision!for factorization homology}
Let $M = M_+ \cup_N M_-$ be a collar-gluing decomposition: $N$ is a
codimension-$1$ manifold with a collar neighborhood in~$M$, and
$M_\pm$ are the two halves. Then there is a natural equivalence
\[
\int_M \mathcal{F}
\;\simeq\;
\int_{M_+} \mathcal{F}
\;\otimes^{\mathbf{L}}_{\int_N \mathcal{F}}\;
\int_{M_-} \mathcal{F}.
\]
\end{theorem}

\subsection{The circle computation by excision}

\begin{theorem}[Factorization homology on $S^1$ $=$ topological Hochschild chains;
\ClaimStatusProvedHere]
\label{thm:circle-fh-hochschild}
\index{factorization homology!circle}
\index{topological Hochschild homology!factorization homology}
Let $\mathcal{F}$ be a locally constant factorization algebra on
$S^1$ with values in $\Ch(k)$, and let $\mathcal{C}$ be the
associated $\Eone$-category \textup{(}the dg-category of modules
over the $\Eone$-algebra $A = \mathcal{F}(I)$ for any interval
$I \subset S^1$\textup{)}. Then there is a natural equivalence
\begin{equation}\label{eq:circle-fh-HH}
\int_{S^1} \mathcal{F}
\;\simeq\;
\mathrm{HH}_\bullet(\mathcal{C})
:= A \otimes^{\mathbf{L}}_{A^e} A,
\end{equation}
where $A^e = A \otimes A^{\mathrm{op}}$.
\end{theorem}

\begin{proof}
The proof proceeds by cutting $S^1$ into overlapping arcs and
applying excision.

\emph{Step~1} (Collar-gluing decomposition of $S^1$).
Choose a decomposition $S^1 = U_+ \cup U_-$ where $U_+$ and $U_-$
are open arcs (each diffeomorphic to an interval) whose intersection
consists of two disjoint intervals:
\[
U_+ \cap U_- = J_1 \sqcup J_2.
\]
Concretely, parametrize $S^1 = \R / \Z$ and take
$U_+ = (0, 3/4)$, $U_- = (1/2, 5/4)$, so that
$J_1 = (1/2, 3/4)$ and $J_2 = (0, 1/4)$ (the latter wrapping around
$0 \equiv 1$). The collar structure along the boundary is given by
the intervals $J_1$ and $J_2$ themselves.

\emph{Step~2} (Local constancy on arcs).
Since $\mathcal{F}$ is locally constant, its value on any interval is
equivalent to the $\Eone$-algebra $A$:
\[
\mathcal{F}(U_+) \simeq A, \quad
\mathcal{F}(U_-) \simeq A, \quad
\mathcal{F}(J_1) \simeq A, \quad
\mathcal{F}(J_2) \simeq A.
\]
More precisely, for each interval $J \subset S^1$, the restriction
$\mathcal{F}|_J$ is equivalent to the factorization algebra associated
to a single $\Eone$-algebra~$A$, and the value $\mathcal{F}(J) \simeq A$
is given by the $\Eone$-structure.

\emph{Step~3} (Excision).
By the excision axiom (Axiom~\ref{thm:excision}) applied to the
collar-gluing $S^1 = U_+ \cup_{J_1 \sqcup J_2} U_-$:
\begin{equation}\label{eq:excision-circle}
\int_{S^1} \mathcal{F}
\;\simeq\;
\mathcal{F}(U_+)
\;\otimes^{\mathbf{L}}_{\mathcal{F}(J_1) \otimes \mathcal{F}(J_2)}\;
\mathcal{F}(U_-).
\end{equation}
Substituting the local constancy identifications from Step~2:
\begin{equation}\label{eq:excision-substituted}
\int_{S^1} \mathcal{F}
\;\simeq\;
A \;\otimes^{\mathbf{L}}_{A^e}\; A,
\qquad A^e := A \otimes A^{\mathrm{op}}.
\end{equation}

\emph{Step~4} (Bimodule structure and identification with HH).
The key is to identify the $A \otimes A$-module structures on the two
copies of~$A$ in~\eqref{eq:excision-substituted}. The inclusions
$J_1 \hookrightarrow U_+$ and $J_2 \hookrightarrow U_+$ give the
left and right $A$-actions on $\mathcal{F}(U_+) \simeq A$: the
inclusion of $J_1$ at one end of the arc~$U_+$ provides the left
action, and the inclusion of $J_2$ at the other end provides the
right action. That these are the \emph{regular} left and right
actions (i.e., $a \cdot_L x = ax$ and $x \cdot_R b = xb$) follows
from local constancy: the factorization algebra~$\mathcal{F}$ on the
arc~$U_+$ is equivalent to the $\Eone$-algebra~$A$ (Step~2), and
the collar inclusions $J_i \hookrightarrow U_+$ restrict to the
identity on~$A$ (since all intervals carry the same algebra by local
constancy). The bimodule structure is therefore
$(a_1, a_2) \cdot x = a_1 \cdot x \cdot a_2$, which is precisely the
diagonal bimodule ${}_A A_A$. Similarly for $\mathcal{F}(U_-)$, where
the \emph{opposite} orientation of $U_-$ relative to $U_+$ introduces
the $A^{\mathrm{op}}$ factor: the left action from $J_1$ on $U_-$
is the right action on $U_+$, and vice versa. This is the source
of the $A^{\mathrm{op}}$ in
$A^e = A \otimes A^{\mathrm{op}}$.

The tensor product over $A \otimes A$ of two copies of the diagonal
bimodule is, by definition, the topological Hochschild chain complex:
\[
A \otimes^{\mathbf{L}}_{A \otimes A^{\mathrm{op}}} A
= A \otimes^{\mathbf{L}}_{A^e} A
=: \mathrm{HH}_\bullet(A).
\]
Here $A \otimes A$ acts on the left copy of~$A$
via $(a_1, a_2) \cdot x = a_1 \cdot x \cdot a_2$
(using the bimodule structure from $J_1$ and $J_2$), and on the
right copy of~$A$ symmetrically; the tensor product over this action
contracts the two bimodules into the cyclic bar complex
$\cdots \to A^{\otimes 3} \to A^{\otimes 2} \to A$ computing
$\mathrm{HH}_\bullet(A)$.

\emph{Step~5} (Passage to the categorical statement).
If $\mathcal{C} = \mathrm{Perf}(A)$ is the dg-category of perfect
$A$-modules, then $\mathrm{HH}_\bullet(\mathcal{C})$ is defined as
$\mathrm{HH}_\bullet(A)$ via the Morita-invariant cyclic bar
construction. Combining with Step~4 gives the stated equivalence
$\int_{S^1} \mathcal{F} \simeq \mathrm{HH}_\bullet(\mathcal{C})$.
\end{proof}

\begin{remark}[Provenance]
\label{rem:annulus-provenance}
The identification of factorization homology on $S^1$ with topological Hochschild
homology is due (in the topological setting) to
Ben-Zvi--Francis--Nadler~\cite{BZFN10} and
Ayala--Francis~\cite{AF15}; in the vertex algebra setting, the
parallel result appears in Costello--Gwilliam~\cite[Chapter~5]{CG17}.
The excision argument above follows the treatment in~\cite{AF15}.
\end{remark}

\subsection{The monodromy subtlety: from chiral to locally constant}
\label{subsec:monodromy-subtlety}

\index{monodromy!factorization homology}

The excision argument of Theorem~\ref{thm:circle-fh-hochschild}
requires $\mathcal{F}$ to be a \emph{locally constant} factorization
algebra on $S^1$. In the chiral algebraic setting, the situation is
more delicate: a chiral algebra~$\cA$ on a curve~$X$ is a
factorization algebra on $X$ that is locally constant on small disks
(the $\Eone$-structure on intervals), but the passage from an interval
to the full circle involves identifying the endpoints. This
identification may carry \emph{monodromy}, a nontrivial automorphism
of the $\Eone$-algebra $A = \cA(I)$ arising from parallel transport
around the puncture.

\begin{definition}[Monodromy automorphism]\label{def:monodromy-aut}
\index{monodromy!automorphism|textbf}
Let $\cA$ be a chiral algebra on a punctured disk $D^\times = D
\setminus \{0\}$, and let $I \subset D^\times$ be an interval.
The fundamental group $\pi_1(D^\times) \cong \Z$ acts on the
fiber $A = \cA(I)$ by monodromy. The \emph{monodromy
automorphism} is the generator:
\[
\mathfrak{m}\colon A \;\xrightarrow{\;\sim\;}\; A,
\]
obtained by analytically continuing sections of $\cA$ around the
puncture once counterclockwise.
\end{definition}

\begin{proposition}[Monodromy for standard families;
\ClaimStatusProvedHere]
\label{prop:monodromy-standard}
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Heisenberg $\mathcal{H}_k$.} The monodromy
 automorphism $\mathfrak{m}$ acts on the mode algebra generated
 by $\{J_n\}_{n \in \Z}$ via $\mathfrak{m}(J_n) = J_n$ for all
 $n$. The monodromy is \emph{trivial} on the algebra. However,
 on Fock modules $F_\lambda$, the monodromy acts by the scalar
 $e^{2\pi i \lambda^2 / (2k)}$
 \textup{(}from the conformal weight $h_\lambda = \lambda^2/(2k)$
 contribution to $q^{L_0}$\textup{)}. For the vacuum module
 $F_0$, this is trivial.
\item \emph{Affine $\widehat{\fg}_k$.} The monodromy is trivial on
 the algebra \textup{(}the current modes $J^a_n$ are
 single-valued\textup{)}. On highest-weight modules $V_\Lambda$ at
 integer level, the monodromy acts by
 $e^{2\pi i h_\Lambda}$ where $h_\Lambda = (\Lambda, \Lambda +
 2\rho) / 2(k + h^\vee)$ is the conformal weight.
\item \emph{Lattice VOA $V_\Lambda$.} The vertex operators
 $e^\alpha$ for $\alpha \in \Lambda$ have monodromy
 $\mathfrak{m}(e^\alpha) = e^{2\pi i (\alpha, \alpha)/2}\, e^\alpha$.
 For an even lattice, $(\alpha, \alpha) \in 2\Z$, so the monodromy
 is trivial. For an odd lattice, the monodromy is a sign
 $(-1)^{(\alpha,\alpha)}$ on each sector (note: odd lattices
 define \emph{super} vertex algebras; the sign is the
 fermion parity).
\end{enumerate}
\end{proposition}

\begin{proof}
In each case, the monodromy is computed from the $L_0$-eigenvalue.
For a primary field $\phi$ of conformal weight~$h$, the operator
product expansion $\phi(e^{2\pi i} z) = e^{2\pi i h} \phi(z)$ gives
the monodromy phase.

(a)~For $\mathcal{H}_k$: the current $J(z) = \sum_n J_n z^{-n-1}$
has conformal weight~$1$, so $J(e^{2\pi i}z) = e^{2\pi i} \cdot
J(z) \cdot e^{-2\pi i} = J(z)$ (the $z^{-n-1}$ factor absorbs the
phase). More precisely, $\mathfrak{m}(J_n) = J_n$ because the modes
are defined as contour integrals $J_n = \oint z^n J(z)\,dz$ over
cycles that are invariant under the monodromy deck transformation.
On $F_\lambda$, the highest-weight vector $|\lambda\rangle$ has
$L_0$-eigenvalue $h_\lambda = \lambda^2/(2k)$, giving the stated
phase.

(b)~Identical argument for $\widehat{\fg}_k$, with $h_\Lambda$
replacing $h_\lambda$.

(c)~For $V_\Lambda$, $e^\alpha$ has conformal weight
$(\alpha,\alpha)/2$, so $\mathfrak{m}(e^\alpha) = e^{2\pi i
(\alpha,\alpha)/2}\, e^\alpha$. For an even lattice,
$(\alpha,\alpha)/2 \in \Z$, so the phase is~$1$.
\end{proof}

\begin{remark}[Twisted topological Hochschild homology]
\label{rem:twisted-hochschild}
\index{topological Hochschild homology!twisted}
When the monodromy $\mathfrak{m}\colon A \to A$ is nontrivial, the
factorization homology on $S^1$ computes the
\emph{$\mathfrak{m}$-twisted topological Hochschild homology}:
\begin{equation}\label{eq:twisted-HH}
\int_{S^1} \mathcal{F}
\;\simeq\;
\mathrm{HH}_\bullet(A;\, {}_{\mathfrak{m}}A)
:= A \otimes^{\mathbf{L}}_{A^e} {}_{\mathfrak{m}}A,
\end{equation}
where ${}_{\mathfrak{m}}A$ is $A$ as a right $A$-module but with
left action twisted by $\mathfrak{m}$: $a \cdot_{\mathfrak{m}} x :=
\mathfrak{m}(a) \cdot x$. The excision argument of
Theorem~\ref{thm:circle-fh-hochschild} goes through verbatim with
$U_-$ contributing the twisted bimodule structure: the analytic
continuation around the full circle inserts $\mathfrak{m}$ into one
of the two collar inclusions.

For the standard families of
Proposition~\ref{prop:monodromy-standard}, the monodromy is trivial
on the algebra itself (the algebra modes are single-valued), so the
untwisted identification~\eqref{eq:circle-fh-HH} holds. The twist
becomes visible only at the module level: the torus partition function
$Z_{T^2}(\cA) = \mathrm{Tr}_{\mathcal{H}}(q^{L_0 - c/24})$ traces
over the Hilbert space~$\mathcal{H}$ with the insertion of
$q^{L_0}$, which is precisely the twist by the monodromy of the
cylinder.
\end{remark}

\begin{remark}[The $(g{=}1, k{=}0)$ modular MC component]
\label{rem:mc-hh-identification}
\index{Maurer--Cartan!genus-1 and topological Hochschild}
The $(g=1, n=0)$ component of the modular MC equation
(Chapter~\ref{ch:en-koszul-duality}) is:
\[
d\Theta_{\cA}^{(1,0)} + \tfrac{1}{2}
 [\Theta_{\cA}^{(0)}, \Theta_{\cA}^{(0)}]^{(1,0)}
 + \Delta_{\mathrm{sew}}\Theta_{\cA}^{(0,2)} = 0.
\]
The sewing operator $\Delta_{\mathrm{sew}}$ contracts two external
legs of $\Theta^{(0,2)}_{\cA}$ using the propagator on the torus.
This is the genus-$1$ topological Hochschild differential: the annulus
amplitude $\Theta^{(0,2)}_{\cA}$ evaluated on two inputs and sewn
into a torus is the trace $\mathrm{Tr}(m_2(-,-))$, the standard
generator of $\mathrm{HH}_0(A)$. The identification of
$\int_{S^1}\cA$ with $\mathrm{HH}_\bullet(A)$
(Theorem~\ref{thm:circle-fh-hochschild})
is therefore the $n=0$ case of the general MC$\to$sewing
correspondence.
\end{remark}

\subsection{Heisenberg verification}

\begin{example}[Topological Hochschild chains of the Heisenberg algebra;
\ClaimStatusProvedHere]
\label{ex:heisenberg-HH-chains}
\index{Heisenberg algebra!topological Hochschild chains}
We verify the identification
$\int_{S^1} \mathcal{H}_k \simeq \mathrm{HH}_\bullet(\mathcal{H}_k)$
against the known genus-$1$ partition function.

\emph{Step~1} (The algebra).
The Heisenberg vertex algebra $\mathcal{H}_k$ at level $k \neq 0$
is generated by a single current $J(z) = \sum_{n \in \Z} J_n
z^{-n-1}$ with OPE $J(z) J(w) \sim k/(z-w)^2$. The mode
algebra is the Weyl algebra on infinitely many generators:
$[J_m, J_n] = k\,m\,\delta_{m+n,0}$. The zero mode $J_0$
acts on the vacuum Fock module $\mathcal{H}_k = F_0$
(with $J_0$-eigenvalue~$0$); the full module category
contains Fock modules $F_\lambda$ for $\lambda \in k^{-1}\Z$.

\emph{Step~2} (Chiral Hochschild homology computation).
By the computation in Example~\ref{ex:E2-heisenberg}:
\[
\mathrm{HH}_\bullet^{\mathrm{ch}}(\mathcal{H}_k)
= \C[c] \otimes \Lambda(\sigma),
\qquad |c| = 2,\; |\sigma| = 1.
\]
The class $c \in \mathrm{HH}_2$ is the Chern class of the level
(the universal deformation class), and $\sigma \in \mathrm{HH}_1$
is the fundamental class of $S^1$ in the cyclic direction.

\emph{Step~3} (Genus-1 partition function).
The factorization homology $\int_{S^1} \mathcal{H}_k
\simeq \mathrm{HH}_\bullet(\mathcal{H}_k)$ computes
topological Hochschild chains. The \emph{torus partition function} is
the Euler characteristic of $\int_{T^2}\mathcal{H}_k$,
which by the sewing formula reduces to
$\mathrm{Tr}_{F_0}(q^{L_0 - c/24})$ where $F_0$ is the
vacuum module (the trace inserts the $q$-grading operator
on the space of states):
\[
Z_{T^2}(\mathcal{H}_k)
= \mathrm{Tr}_{F_0}(q^{L_0 - 1/24})
= q^{-1/24} \prod_{n=1}^{\infty} \frac{1}{1 - q^n}
= \frac{1}{\eta(\tau)},
\]
where $\eta(\tau) = q^{1/24} \prod_{n \geq 1}(1-q^n)$ is the
Dedekind eta function.

\emph{Step~4} (Consistency check: $\mathrm{HH}_0$).
The degree-$0$ topological Hochschild homology $\mathrm{HH}_0(\mathcal{H}_k) =
A / [A, A]$ is the abelianization of the mode algebra. For the Weyl
algebra generated by $\{J_n\}$, all commutators $[J_m, J_n] = km\,
\delta_{m+n,0}$ are scalar, so $A / [A, A]$ is the symmetric algebra
on the generators modulo the scalars: $\mathrm{HH}_0 \cong \C$
(one-dimensional, generated by the vacuum class). This is consistent
with the partition function $Z_{T^2}$ being a single function
(not a vector): the space of conformal blocks on the torus is
one-dimensional for the Heisenberg algebra at any level.

\emph{Step~5} (Comparison with Theorem~\ref{thm:partition-cyclic}).
The cyclic homology $\mathrm{HC}_0(\mathcal{H}_k) = \C$ matches the
one-dimensional space of genus-$1$ conformal blocks. The full
topological Hochschild chain complex $\mathrm{HH}_\bullet(\mathcal{H}_k) = \C[c]
\otimes \Lambda(\sigma)$ encodes the deformation theory of the torus
partition function: $c$ controls the variation of $Z_{T^2}$ with
respect to the level~$k$, and $\sigma$ represents the circle
direction in the torus.
\end{example}

\begin{remark}[Annulus vs torus]
\label{rem:annulus-vs-torus}
\index{annulus!vs torus}
The factorization homology $\int_{S^1} \mathcal{F}$ over the circle
gives the topological Hochschild chains $\mathrm{HH}_\bullet(A)$. The partition
function on the torus $T^2 = S^1 \times S^1$ involves a further
circle integral, which gives the cyclic homology
$\mathrm{HC}_\bullet(A)$ (the $S^1$-equivariant version of
$\mathrm{HH}_\bullet$). Schematically:
\[
\int_{S^1} \mathcal{F} = \mathrm{HH}_\bullet(A),
\qquad
\int_{T^2} \mathcal{F}
= \mathrm{HC}_\bullet(A)
= \mathrm{HH}_\bullet(A)_{hS^1}.
\]
The first circle is the spatial circle (excision gives HH); the second
is the thermal circle (the $S^1$-action on HH gives HC).
For the Heisenberg:
$\mathrm{HC}_0(\mathcal{H}_k) = \C$, and the character
$\mathrm{Tr}_{F_0}(q^{L_0-c/24}) = 1/\eta(\tau)$ is the
generating function for the graded dimensions of the cyclic complex.
\end{remark}

\begin{remark}[Relation to Theorem~C \textup{(}complementarity\textup{)}]
\label{rem:annulus-complementarity}
\index{complementarity!annulus}
The topological Hochschild chain identification provides the genus-$1$ input to
the complementarity theorem
(Theorem~\ref{thm:quantum-complementarity-main}). At genus~$1$, the
complementarity formula reads
$Q_1(\cA) \oplus Q_1(\cA^!) \cong H^*(\overline{\mathcal{M}}_{1,1},
\mathcal{Z}(\cA))$.
The left-hand side is computed by topological Hochschild chains of $\cA$ and
$\cA^!$ respectively (via the annulus identification); the right-hand
side is the cohomology of the moduli space with coefficients in the
center sheaf. The complementarity is the statement that the two
topological Hochschild chain complexes assemble into a complete basis for the
modular functor at genus~$1$.
\end{remark}

\subsection{Summary and future directions}

The theoretical arc of Part~\ref{part:bar-complex} is now complete. Algebraic foundations (\S\ref{ch:algebraic-foundations}) supplied the operadic language; configuration spaces (\S\ref{chap:config-spaces}) gave it geometric content; the bar-cobar adjunction (Theorem~A) and the Verdier intertwining $D_{\mathrm{Ran}}(B(\cA)) \simeq B(\cA^!)$ established duality on the Ran space; and the higher-genus theory assembled the proved scalar package~$\kappa(\cA)$, the proved spectral package~$(\Delta_{\cA},\Pi_{\cA})$, and the bar-intrinsic Maurer--Cartan element~$\Theta_{\cA}$. The three main theorems (adjunction~(A), inversion on the Koszul locus~(B), and Lagrangian complementarity~(C)) are projections of a single structure: the modular Koszul object associated to a factorization algebra on curves. Chiral Hochschild cohomology, developed in this chapter, is the infinitesimal invariant of that structure: concentrated in degrees $\{0,1,2\}$ for Koszul algebras (Theorem~H), it classifies deformations, detects obstructions, and exchanges under Koszul duality via the Connes operator.

The modular characteristic~$\kappa(\cA)$ is only the linear leading term of this structure. Part~\ref{part:characteristic-datum} extracts the full nonlinear content: the shadow obstruction tower $\kappa(\cA) \to \Delta \to \mathfrak{C} \to \mathfrak{Q} \to \cdots$, a hierarchy of finite-order invariants whose all-degree limit is the universal class~$\Theta_\cA$.
