% !TEX root = ../../main.tex
% ================================================================
% Koszulness moduli object: fourteen chart tests on the associator torsor
% Vol I classification chapter. Canonical inscription of the
% Kontsevich--Tamarkin reformulation of chiral Koszul duality.
% ================================================================

\chapter{The Koszulness moduli object}
\label{v1-ch:koszulness-moduli-scheme}

\section{Orientation: from Koszul tests to a moduli object}
\label{v1-sec:kms-orientation}

The fourteen chart tests for chiral Koszulness of a chiral algebra
$\cA$ on a smooth algebraic curve~$X$ with PBW filtration have
four mathematical origins: homological algebra, deformation
theory, factorisation geometry, and tropical geometry. Read at
the Knizhnik--Zamolodchikov associator they appear with unequal
scope. Read as chart tests on the associator torsor, the scope is
part of the coordinate, not part of the algebra.

The naive set-valued moduli problem is the $\pi_0$ shadow of
the derived deformation problem. Its points are
associator coordinates together with a deformation of the universal
twisting morphism and a null-homotopy of the corresponding
Koszul cone. Its framed finite PBW truncations are classical open
subschemes cut out by Fitting ideals of cohomology; its unframed
finite truncations are derived Artin quotient stacks; its completed
object is pro-formal. The fourteen classical criteria are fourteen
named chart tests on this object, each centred at an explicit
associator coordinate $\Phi_j \in \mathrm{Assoc}(\bQ)$ and each
requiring a comparison quasi-isomorphism with the finite Koszul cone.
The word ``moduli'' therefore names four related carriers:
a derived formal functor in Artinian dg directions, a derived
Artin quotient stack before gauge framing, a framed finite-stage
derived affine scheme, and a finite-window test object inside a
fixed PBW truncation. They are not interchangeable.

Section~\ref{v1-sec:kms-moduli} constructs the completed
Koszulness moduli functor
$\cM_{\mathrm{Kosz}}(\cA)$ and proves the precise finite-type
statement behind the word ``moduli''
(Theorem~\ref{v1-thm:kms-moduli}); the proof uses the
Kontsevich--Tamarkin transfer
in~\cite{Kontsevich99,Tamarkin03} as its operadic input and
standard tangent-obstruction theory for Maurer--Cartan
functors as its deformation-theoretic input.
Section~\ref{v1-sec:kms-atlas} assembles the fourteen charts,
each verified at its own associator coordinate, and proves
that an admissible chart predicate is equivalent to completed
Koszulness on the locus where its comparison complex computes
the Koszul cone
(Theorem~\ref{v1-thm:kms-fourteen-unconditional}); this identifies
both the coordinate dependence and the comparison hypothesis.
Section~\ref{v1-sec:kms-frontier-closures} applies the atlas to
two frontier items: the non-circular Virasoro Koszulness proof
at the Hodge--Betti chart
(Theorem~\ref{v1-thm:kms-virasoro-noncircular})
and the Yangian chart inclusion
(Theorem~\ref{v1-thm:kms-yangian-embedding}). Section~\ref{v1-sec:kms-meta}
records the meta-Koszulness theorem
(Theorem~\ref{v1-thm:kms-meta-koszulness}): the finite-stage
tangent category of admissible charts carries an
$\Etwo$-structure from $\mathrm{GRT}_1$, compatible with PBW
completion under the Mittag--Leffler hypothesis.

Three firewalls are fixed. First,
$\cM_{\mathrm{Kosz}}(\cA)$ is derived and completed unless a
finite-stage hypothesis is explicitly imposed. Second,
the five objects
\[
\cA,\qquad
\barBch(\cA),\qquad
\cA^{\mathrm{i}}=H^\bullet(\barBch(\cA)),\qquad
\cA^!=(\cA^{\mathrm{i}})^\vee,\qquad
\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)
=\ChirHoch^*(\cA,\cA)
\]
are never identified. The equivalence
$\Omega^{\mathrm{ch}}\barBch(\cA)\simeq \cA$ is bar--cobar
inversion; $\cA^!$ is obtained by Verdier duality from
$\cA^{\mathrm{i}}$; the closed-sector object is the chiral Hochschild
derived centre. Strict Koszul duality is the contravariant
duality between augmented Koszul objects after the Koszul cone is
acyclic; it is not the counit map and not the Verdier operation
alone. Physical bulk comparisons factor through an explicitly
named closed-sector object, usually
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$, and never through
$\barBch(\cA)$ by abbreviation. Third, the derived centre carrying
$\Etwo$-structure in the meta-Koszulness theorem is the right
adjoint to an underlying functor, not a categorified averaging
operation.

\begin{remark}[Native versus derived $E_n$]
\label{v1-rem:kms-native-vs-derived-en}
Throughout this chapter, $\cA$ is an $\Eone$-chiral algebra by
hypothesis. Higher $E_n$-structure appears only on its
\emph{derived centre} $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA) =
\ChirHoch^*(\cA,\cA)$ and on the Koszulness moduli object
$\cM_{\mathrm{Kosz}}(\cA)$ itself. The Kontsevich integral
chart $U_{14}$ witnesses homotopy-Koszulity of
$\SCchtop$ on the derived centre pair
$(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA),\cA)$, not on~$\cA$
itself. \end{remark}

% ================================================================
\section{The Koszulness moduli object}
\label{v1-sec:kms-moduli}
% ================================================================

\subsection{Finite-window carriers}

The inputs to the construction are
\begin{itemize}
\item a chiral algebra~$\cA$ on~$X$ with PBW filtration
 $F_\bullet \cA$ whose associated graded
 $R_\cA = \gr^F\!\cA$ is a Poisson vertex algebra;
\item the chiral bar complex
 $\barBch(\cA) = T^c(s^{-1}\bar\cA)$ with deconcatenation
 coproduct, augmentation ideal
 $\bar\cA = \ker(\varepsilon)$, desuspension
 $|s^{-1}v| = |v|-1$;
\item the cobar functor $\Omega^{\mathrm{ch}}$ and the counit
 $\varepsilon_\cA \colon
 \Omega^{\mathrm{ch}}(\barBch(\cA)) \to \cA$.
\end{itemize}

The \emph{Koszul locus} is the set of~$\cA$ on which
$\varepsilon_\cA$ is a quasi-isomorphism. A criterion for this
locus is a theorem only after its augmentation, coalgebra
completion, twisting morphism, finite-stage counit, and
spectral-sequence convergence have all been named.

All moduli statements below use the PBW completion. Write
$F_{\le N}\barBch(\cA)$ for the finite PBW truncation and
$\widehat{\barBch}(\cA)=\varprojlim_N F_{\le N}\barBch(\cA)$.
The algebra~$\cA$ is of \emph{finite PBW type} when every
$F_{\le N}\barBch(\cA)$ and $F_{\le N}\cA$ is a perfect complex
of $\bQ$-vector spaces with uniformly bounded cohomological
amplitude on compact subsets of the parameter space, and the
transition maps in~$N$ satisfy the Mittag--Leffler condition.
Without this hypothesis the object below is still a derived
formal functor; its classical truncation need not be a scheme of
finite type.

The finite-stage representability statement uses one further
hypothesis. At PBW stage~$N$ and weight quotient~$m$ of
$\mathrm{GRT}_1$, write
$\mathfrak g_{\Phi,N,m}(\cA)$ for the corresponding finite
quotient of the convolution dg Lie algebra. The pair
$(\cA,N,m)$ is of \emph{PBW--Artin type} if
\begin{enumerate}[label=\textup{(\alph*)}]
\item $\mathfrak g_{\Phi,N,m}(\cA)$ is a nilpotent dg Lie
 algebra with finite-dimensional cohomology and bounded
 amplitude;
\item the gauge group
 $\exp(\mathfrak g_{\Phi,N,m}^0(\cA))$ is an algebraic
 unipotent group acting on the finite Maurer--Cartan scheme;
\item the finite Koszul cone
 $C_{\Phi,N,m}$ is perfect and its cohomology sheaves are coherent;
\item the inverse system in~$N$ is derived Mittag--Leffler, so
 ordinary inverse limits compute derived inverse limits.
\end{enumerate}
Under PBW--Artin type the unframed finite-stage moduli is a
derived Artin quotient stack
$[\mathrm{MC}(\mathfrak g_{\Phi,N,m})/\exp(\mathfrak g_{\Phi,N,m}^0)]$
restricted to the open acyclicity locus. After fixing an
associator coordinate and a gauge framing it becomes an open
derived affine scheme. The word \emph{scheme} below always refers
to this framed finite-stage object.

\begin{definition}[Finite-window Koszul test]
\label{v1-def:kms-finite-window-test}
\ClaimStatusProvedHere
Fix an associator~$\Phi$, a PBW stage~$N$, and a finite weight
quotient~$m$ of $\mathrm{GRT}_1$. A \emph{finite-window Koszul
test} for~$\cA$ is the tuple
\[
\mathsf K_{\Phi,N,m}(\cA)=
\bigl(\varepsilon,F_{\le N}\barBch(\cA),
\tau_{\Phi,N,m},\varepsilon_{\Phi,N,m},
C_{\Phi,N,m},E_r^{\Phi,N,m}\bigr)
\]
with the following typed data.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
\item $\varepsilon\colon \cA\to\omega_X$ is the fixed
 augmentation and
 $\bar\cA=\ker(\varepsilon)$; changing the augmentation changes
 the test.
\item $F_{\le N}\barBch(\cA)=F_{\le N}T^c(s^{-1}\bar\cA)$ is a
 counital conilpotent factorisation coalgebra. The completed
 object
 $\widehat{\barBch}(\cA)=\varprojlim_NF_{\le N}\barBch(\cA)$ is
 used only in the pro-conilpotent category with continuous
 coalgebra maps.
\item
 $\tau_{\Phi,N,m}\colon F_{\le N}\barBch(\cA)\to F_{\le N}\cA$
 is a $\Phi$-coordinate twisting morphism, equivalently a
 Maurer--Cartan element of
 $\mathfrak g_{\Phi,N,m}(\cA)$.
\item The finite-stage counit
 \[
 \varepsilon_{\Phi,N,m}\colon
 \Omega^{\mathrm{ch}}_{\Phi}
 \bigl(F_{\le N}\barBch(\cA),\tau_{\Phi,N,m}\bigr)
 \longrightarrow F_{\le N}\cA
 \]
 is the map whose cone
 $C_{\Phi,N,m}:=\operatorname{Cone}(\varepsilon_{\Phi,N,m})$
 tests Koszulness at this window.
\item $E_r^{\Phi,N,m}$ is the spectral sequence induced by the
 PBW and coradical filtrations on~$C_{\Phi,N,m}$. It is required
 to be bounded and strongly convergent at the finite window, and
 the inverse system in~$N$ is required to be derived
 Mittag--Leffler before any completed criterion is asserted.
\end{enumerate}
A chart predicate is \emph{admissible} only if it is the
acyclicity of a perfect test complex~$T_{\Phi,N,m}$ equipped
with a filtered quasi-isomorphism
$T_{\Phi,N,m}\xrightarrow{\sim}C_{\Phi,N,m}$ compatible with
the transition maps in~$N$ and~$m$.
\end{definition}

\begin{definition}[Koszulness moduli object]
\label{v1-def:kms-moduli-scheme}
\ClaimStatusProvedHere
For a complete local Artinian commutative dg
$\bQ$-algebra~$R$ with maximal ideal~$\mathfrak m_R$, set
\[
\widehat{\mathfrak g}_\Phi(\cA)
=
\varprojlim_N
\mathrm{Conv}_\Phi
\bigl(F_{\le N}\barBch(\cA),F_{\le N}\cA\bigr),
\]
the completed convolution dg Lie algebra whose
Maurer--Cartan equation is the $\Phi$-coordinate twisting
equation for the bar-cobar counit. The \emph{Koszulness
moduli object} is the derived functor
\[
\cM_{\mathrm{Kosz}}(\cA)\colon
\mathbf{Art}^{\wedge}_{\bQ}
\longrightarrow \mathbf{Spaces},
\]
\[
R\longmapsto
\operatorname{hofib}_{0}
\left[
\coprod_{\Phi\in\mathrm{Assoc}(R)}
\mathrm{MC}_{\bullet}\bigl(\widehat{\mathfrak g}_\Phi(\cA)
\widehat{\otimes}\mathfrak m_R\bigr)
\xrightarrow{\;\xi\mapsto\operatorname{Cone}(\varepsilon_\xi)\;}
D^{\mathrm{co}}_{\mathrm{ch}}(X;R)
\right].
\]
Equivalently, an $R$-point may be written
$(\Phi,\xi,h_\xi)$, where
$\Phi\in\mathrm{Assoc}(R)$,
$\xi\in
\mathrm{MC}_{\bullet}(\widehat{\mathfrak g}_\Phi(\cA)
\widehat{\otimes}\mathfrak m_R)$, and
$h_\xi$ is a trivialisation of
$\operatorname{Cone}(\varepsilon_\xi)$ in the coderived
chiral category over~$R$. The displayed homotopy fibre is a
space; it is not a set of representatives modulo an implicit
equivalence relation.
Here $\varepsilon_\xi\colon
\Omega^{\mathrm{ch}}_\Phi(\widehat{\barBch}(\cA),\xi)\to
\cA\widehat{\otimes}R$ is the counit deformed by~$\xi$.
A chart coordinate at~$\Phi$ is a triple
$(\Pi_\Phi,\mathrm{wit}_\Phi,\gamma_\Phi)$ consisting of
\begin{enumerate}[label=\textup{(\alph*)}]
\item a Koszulness predicate $\Pi_\Phi$ depending only on the
 pair $(\cA,\Phi)$ and expressible as acyclicity of a perfect
 test complex $T_{\Phi,N,m}$ at every finite PBW stage and
 finite weight quotient, together
 with a filtered comparison quasi-isomorphism
 $q_{\Phi,N,m}\colon T_{\Phi,N,m}\xrightarrow{\sim}
 C_{\Phi,N,m}$;
\item a witness $\mathrm{wit}_\Phi(\cA)$ in the test category
 fixed by~$\Phi$, equivalently a compatible system of
 null-homotopies
 $h_{\Phi,N,m}\colon T_{\Phi,N,m}\simeq 0$ whose images
 under~$q_{\Phi,N,m}$ trivialise the Koszul cones;
\item a transition $1$-cocycle
 $\gamma_\Phi\colon \Phi \leadsto \Phi'$ to every other
 associator~$\Phi'$, satisfying the Tamarkin
 compatibility~\cite{Tamarkin03}:
 \[
 T_{\Phi,N,m}\simeq 0
 \;\iff\;
 T_{\Phi\cdot g,N,m}\simeq 0
 \qquad \text{for every } g \in \mathrm{GRT}_1(R).
 \]
\end{enumerate}
\end{definition}

Each associator~$\Phi$ fixes a formality coordinate for
little two-disks. The KZ PBW spectral sequence, the
Alekseev--Torossian Kashiwara--Vergne complex, the
Hodge--Betti weight filtration, the elliptic KZB coordinate,
and the Kontsevich integral are five different coordinate
systems on the same completed deformation problem. The
transition cocycle is the Tamarkin $\Phi$-transfer:
a filtered quasi-isomorphism of convolution dg Lie algebras.
Over a point,
$\mathrm{Assoc}(\bC)$ is the pro-unipotent torsor
$\exp(\widehat{\mathfrak{grt}}_1(\bC))$; after finite
PBW and weight truncation, the corresponding Koszul locus is
classical and locally of finite type only in a framed coordinate.
Without the framing it is the quotient stack by the unipotent
gauge group.

\begin{theorem}[Koszulness moduli, finite-stage representability]
\label{v1-thm:kms-moduli}
\ClaimStatusProvedHere
Let $\cA$ be a chiral algebra on~$X$ of finite PBW type, and
assume PBW--Artin type at every finite pair~$(N,m)$ used below.
Then $\cM_{\mathrm{Kosz}}(\cA)$ is a possibly empty derived
formal moduli problem over the Drinfeld associator torsor. For
each finite PBW stage~$N$ and finite weight quotient~$m$ of
$\mathrm{GRT}_1$, the unframed finite-stage truncation is a
derived Artin quotient stack; after fixing an associator
coordinate and a gauge framing, its classical truncation is an
open subscheme of a finite-type affine Maurer--Cartan scheme.
The closed complement is cut out by the Fitting ideals of the
cohomology of the finite Koszul cone. The completed moduli
object is the derived inverse limit of these finite stages, and
under the Mittag--Leffler hypothesis this is the ordinary
PBW-completed inverse limit. It should be read as an honest
affine scheme of finite type only after framing and finite-stage
stabilization of the PBW tower. It has the following properties.
\begin{enumerate}[label=\textup{(A\arabic*)},leftmargin=3em]
\item\label{v1-item:kms-A1}
 $\cM_{\mathrm{Kosz}}(\cA) \neq \emptyset$ if and only if
 the completed counit
 $\Omega^{\mathrm{ch}}(\widehat{\barBch}(\cA))\to\cA$
 is a quasi-isomorphism, equivalently the finite-stage counits
 $\varepsilon_{\Phi,N,m}$ of
 Definition~\ref{v1-def:kms-finite-window-test} have acyclic
 cones for all~$N,m$ and the PBW tower is derived
 Mittag--Leffler. This property is
 $\mathrm{GRT}_1$-invariant: it is a property of~$\cA$, not
 of a choice of associator.
\item\label{v1-item:kms-A2}
 At a point $x=(\Phi,\xi,h_\xi)$ with cone~$C_\xi$, the
 tangent-obstruction complex is
 \[
 \mathbb T_x\cM_{\mathrm{Kosz}}(\cA)
 \simeq
 \operatorname{fib}\!\left(
 \mathfrak{grt}_1
 \oplus
 \widehat{\mathfrak g}_\Phi(\cA)^\xi
 \xrightarrow{\;D_{\xi}\;}
 \mathrm{RHom}(C_\xi,C_\xi)[1]
 \right)[1].
 \]
 Here $D_\xi$ differentiates the Koszul cone. First-order
 chart deformations are $H^0(\mathbb T_x)$, and obstruction
 classes lie in $H^1(\mathbb T_x)$; equivalently they are
 $H^1$ and $H^2$ of the controlling fibre dg Lie algebra before
 the final shift.
\item\label{v1-item:kms-A3}
 On the nonempty Koszul support, each \emph{framed} component
 obtained from a base witness
 $c_0\in\mathrm{Chart}_{\Phi_{\mathrm{KZ}}}(\cA)$ is a
 pro-$\mathrm{GRT}_1$-torsor over the associator torsor. At
 finite weight quotient~$m$ it is a principal
 $\mathrm{GRT}_{1,\le m}$-bundle. Before framing, the same
 component is the quotient of this torsor by the automorphism
 group of the witness; stabilizers are governed by the negative
 cohomology of the controlling dg Lie algebra. Transitions
 between charts are Tamarkin $\Phi$-transfer maps, and the
 cocycle condition closes on each component.
\item\label{v1-item:kms-A4}
 On each nonempty component, the fourteen classical
 characterisations listed in the atlas below form a finite
 system of admissible derived open chart tests:
 $U_1,\ldots,U_{10}$ are centred at $\Phi_{\mathrm{KZ}}$;
 $U_{11}$ at $\Phi_{\mathrm{AT}}$ (Alekseev--Torossian);
 $U_{12}$ at $\Phi_{\mathrm{dR,B}}$ (de Rham--Betti);
 $U_{13}$ at $\Phi_{\mathrm{ell}}$ (Enriquez elliptic); and
 $U_{14}$ at $\Phi_{\mathrm{Kon}}$ (Kontsevich integral).
\item\label{v1-item:kms-A5}
 The shadow-class stratification
 $\mathrm{G} \sqcup \mathrm{L} \sqcup \mathrm{C}
 \sqcup \mathrm{M} \sqcup \mathrm{FF}$ lifts to a
 stratification
 \[
 \cM_{\mathrm{Kosz}}(\cA)
 = \bigsqcup_{c\,\in\,\{G,L,C,M,FF\}}
 \cM^{(c)}_{\mathrm{Kosz}}(\cA),
 \]
 with distinguished chart $\Phi_{\mathrm{KZ}}$ on~$\mathrm{G}$
 and on the generic Kac--Moody locus of~$\mathrm{L}$,
 $\Phi_{\mathrm{ell}}$ on the modular locus of~$\mathrm{L}$,
 $\Phi_{\mathrm{AT}}$ on~$\mathrm{C}$, $\Phi_{\mathrm{Kon}}$
 on~$\mathrm{M}$, and $\Phi_{\mathrm{dR,B}}$ on~$\mathrm{FF}$.
 At finite PBW stage the strata are locally closed substacks
 defined by rank conditions on the shadow bracket maps; the
 completed strata are their inverse limits.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{\ref{v1-item:kms-A1}.} Chiral Koszulness is the
acyclicity of the cone of the counit
$\Omega^{\mathrm{ch}}\widehat{\barBch}(\cA)\to\cA$, equivalently
the acyclicity of the twisted tensor product
$K^L_\tau(\cA,\widehat{\barBch}(\cA))$ for the universal
twisting morphism
$\tau\colon \widehat{\barBch}(\cA)\to\cA$
\cite{LV12,Positselski11}. The Tamarkin transfer sends
$\widehat{\mathfrak g}_{\Phi}(\cA)$ to
$\widehat{\mathfrak g}_{\Phi\cdot g}(\cA)$ by a filtered
quasi-isomorphism and carries $C_{\Phi,N,m}$ to
$C_{\Phi\cdot g,N,m}$ for every finite~$(N,m)$
\cite{Kontsevich99,Tamarkin03}. Acyclicity of a cone is
preserved by filtered quasi-isomorphism and by the
Mittag--Leffler inverse limit. Thus nonemptiness is exactly
completed chiral Koszulness, and the assertion is independent
of the associator coordinate.

\emph{\ref{v1-item:kms-A2}.}
The deformation functor of a complete dg Lie algebra has tangent
complex $\mathfrak g^\xi[1]$ at an MC point~$\xi$. The associator
coordinate contributes $\mathfrak{grt}_1[1]$. The Koszul
condition is not an extra discrete predicate; it is the derived
vanishing condition on the cone~$C_\xi$. Differentiating the
assignment $\xi\mapsto C_\xi$ gives
\[
D_\xi\colon
\mathfrak{grt}_1\oplus
\widehat{\mathfrak g}_\Phi(\cA)^\xi
\longrightarrow
\mathrm{RHom}(C_\xi,C_\xi)[1].
\]
Taking the homotopy fibre imposes the infinitesimal condition
that the null-homotopy~$h_\xi$ deform with~$\xi$. This gives the
displayed tangent complex. The usual obstruction theory for
small extensions of Artinian dg algebras identifies first-order
deformations with $H^0$ of this tangent complex and obstructions
with $H^1$.

\emph{\ref{v1-item:kms-A3}.}
Assume that $\cM_{\mathrm{Kosz}}(\cA;R)$ is nonempty. Fix the base
point $\Phi_0=\Phi_{\mathrm{KZ}}$ and a base witness
$c_0\in\mathrm{Chart}_{\Phi_0}(\cA;R)$. The
Grothendieck--Teichm\"uller torsor produces, after finite weight
quotient and then by inverse limit, the unique element
$g_\Phi$ carrying $\Phi_0$ to~$\Phi$. The Tamarkin transfer
\[
g_\Phi^*\colon
\mathrm{Chart}_{\Phi_0}(\cA;R)
\xrightarrow{\;\;\sim\;\;}
\mathrm{Chart}_\Phi(\cA;R)
\]
is an equivalence of derived chart groupoids. After a gauge
framing, the component generated by~$c_0$ consists of the
transported witnesses $g_\Phi^*(c_0)$ and is therefore a
principal $\mathrm{GRT}_{1,\le m}$-bundle at finite weight
quotient~$m$. Removing the framing divides by automorphisms of
the MC point and of the null-homotopy; these automorphisms are
the stabilizer stack computed by the negative cohomology of the
controlling fibre dg Lie algebra. The cocycle condition is the
associativity of composition in $\mathrm{GRT}_1$ and holds at
every finite quotient, hence in the completion.

\emph{\ref{v1-item:kms-A4}.}
The KZ chart tests~(i)--(x) are stated in the KZ language
(PBW spectral sequence, bar cohomology
concentration, $\Ainfty$-formality of the KZ model,
Barr--Beck--Lurie monadicity, etc.): they therefore sit at
$\Phi_{\mathrm{KZ}}$. The four supplementary charts
$U_{11},\ldots,U_{14}$ are produced in
Propositions~\ref{v1-prop:kms-at-chart},
\ref{v1-prop:kms-hodge-betti-chart},
\ref{v1-prop:kms-elliptic-chart}, and
\ref{v1-prop:kms-kontsevich-chart}, each proved at its
own associator. In each admissible chart there is a
finite-window Koszul test $\mathsf K_{\Phi,N,m}(\cA)$, a perfect
test complex $T_{\Phi,N,m}$, and a filtered comparison
quasi-isomorphism $T_{\Phi,N,m}\simeq C_{\Phi,N,m}$. At finite
PBW stage and finite weight quotient, acyclicity of
$T_{\Phi,N,m}$ is therefore acyclicity of the finite Koszul cone.
The locus on which it is acyclic is open; its complement is
closed, cut out by the Fitting ideals of
$H^\bullet(C_{\Phi,N,m})$. Passing to the filtered inverse
limit gives the completed derived open chart only under the
derived Mittag--Leffler hypothesis. Pairwise
compatibility of admissible charts is the torsor statement
of~\ref{v1-item:kms-A3}. Off the Koszul support all chart
fibres are empty.

\emph{\ref{v1-item:kms-A5}.}
The shadow class is an intrinsic invariant of the
Maurer--Cartan element $\Theta_\cA$; it is therefore a
partition of the set of chirally Koszul algebras, and it lifts
at finite PBW stage to locally closed substacks of
$\cM_{\mathrm{Kosz}}(\cA)$. Shadow depth and bracket rank are
rank conditions on the structure maps defining~$\Theta_\cA$.
The completed stratum is the inverse limit of these locally
closed finite strata. The distinguished chart on each stratum is
determined by the computational complexity of the shadow algebra
bracket there:
\begin{itemize}
\item class~$\mathrm{G}$ (Heisenberg-type, $r_{\max}=2$):
 abelian shadow bracket, $\Phi_{\mathrm{KZ}}$ is the flat
 connection on $\FM_n(\bC)$ and $U_1$ is trivially satisfied;
\item class~$\mathrm{L}$ (affine Kac--Moody, $r_{\max}=3$):
 cubic bracket activates at genus one,
 $\Phi_{\mathrm{ell}}$ has modular equivariance built in;
\item class~$\mathrm{C}$ (free first-order systems,
 $r_{\max}=4$): contact termination at~$S_4$ diagonalises
 under $\Phi_{\mathrm{AT}}$ (Kashiwara--Vergne data, see
 Proposition~\ref{v1-prop:kms-at-chart});
\item class~$\mathrm{M}$ (Virasoro, $\cW_N$, $r_{\max}=\infty$):
 $\Phi_{\mathrm{Kon}}$ tracks the full Maurer--Cartan
 expansion through chord diagrams;
\item class~$\mathrm{FF}$ (Feigin--Frenkel, critical level
 $k=-h^\vee$): the de Rham--Betti chart sees purity via
 BGG resolution, $\Phi_{\mathrm{dR,B}}$ is the natural
 coordinate.
\end{itemize}
\end{proof}

\begin{corollary}[Associator-independence of the Koszulness
property]
\label{v1-cor:kms-grt-invariant}
\ClaimStatusProvedHere
The property $[\cA$ completed-chirally Koszul$]
= [\cM_{\mathrm{Kosz}}(\cA) \neq \emptyset]$ is
$\mathrm{GRT}_1$-invariant. What depends on the choice of
associator is the \emph{characterisation}: the specific
predicate $\Pi_\Phi$ that witnesses Koszulness. An admissible
classical characterisation is equivalent to completed Koszulness
on its home $\Phi$-chart because its comparison complex computes
the Koszul cone; the scoped KZ formulations are restrictions of
these chart-local statements to the KZ coordinate.
\end{corollary}

\begin{proof}
Immediate from Theorem~\ref{v1-thm:kms-moduli}\ref{v1-item:kms-A1}
(property is $\mathrm{GRT}_1$-invariant)
combined with Theorem~\ref{v1-thm:kms-fourteen-unconditional}
(each admissible chart is equivalent on its home associator).
\end{proof}

\begin{remark}[Kontsevich--Tamarkin, operational form]
\label{v1-rem:kms-kt-operational}
The classical Kontsevich--Tamarkin theorem asserts, over a
field of characteristic zero, that the little two-disks
operad $\mathbf{E}_2$ is formal, with the formality
isomorphism depending on a choice of Drinfeld associator.
The Koszulness moduli object gives this statement operational
content at the level of a single algebra: chiral Koszulness is
$\mathrm{GRT}_1$-invariant; admissible classical
characterisations are coordinates over the associator torsor;
switching between two admissible criteria is an application of
the Tamarkin transfer, together with the comparison
quasi-isomorphisms to the Koszul cone.
\end{remark}

% ================================================================
\section{The fourteen charts and their home-coordinate status}
\label{v1-sec:kms-atlas}
% ================================================================

The atlas has fourteen chart tests. Entries $U_1,\ldots,U_{10}$
are the KZ entries at $\Phi_{\mathrm{KZ}}$, taken verbatim from
Chapter~\ref{chap:koszul-pair-structure} with their home
coordinate made explicit. The additional four are stated
here as independent propositions at $\Phi_{\mathrm{AT}}$,
$\Phi_{\mathrm{dR,B}}$, $\Phi_{\mathrm{ell}}$, and
$\Phi_{\mathrm{Kon}}$, each with its own comparison complex. The
argument does not promote a scoped KZ criterion by fiat:
each supplementary chart must identify its test complex with the
finite Koszul cone at its own associator.

\begin{theorem}[Fourteen admissible characterisations on their home chart]
\label{v1-thm:kms-fourteen-unconditional}
\ClaimStatusProvedHere
Let $\cA$ be a chiral algebra on~$X$ of finite PBW type, and
assume the PBW--Artin hypotheses at the finite stages appearing
below. The following fourteen predicates are chart tests. On the locus
where the named finite-stage comparison complex
$T_{\Phi,N,m}$ exists and the maps
$T_{\Phi,N,m}\xrightarrow{\sim}C_{\Phi,N,m}$ are filtered
quasi-isomorphisms compatible with PBW completion, the predicate
is equivalent to completed chiral Koszulness of~$\cA$ on its home
associator coordinate. Outside that admissible locus, the
predicate remains a test condition and is not asserted to be
equivalent to Koszulness.

\smallskip
\noindent\textup{(} \emph{Home coordinate}
$\Phi_{\mathrm{KZ}}$, charts $U_1$--$U_{10}$\textup{):}
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
\item $U_1$ \emph{(PBW $\Etwo$-collapse):}
 the PBW spectral sequence of
 $\barBch(\cA)$ collapses at $\Etwo$.
\item $U_2$ \emph{(chiral Koszul morphism):}
 the counit
 $\Omega^{\mathrm{ch}}(\widehat{\barBch}(\cA)) \to \cA$ is a
 quasi-isomorphism.
\item $U_3$ \emph{($\Ainfty$-formality of the KZ model):}
 the minimal $\Ainfty$-model of~$\cA$ at $\Phi_{\mathrm{KZ}}$
 has $m_k=0$ for $k\geq 3$.
\item $U_4$ \emph{(shadow-tower formality):}
 the shadow tower $\Theta_\cA$ is formal as an
 $\Linfty$-algebra at the $\Phi_{\mathrm{KZ}}$ base.
\item $U_5$ \emph{($\Etwo$-formality of chiral Hochschild):}
 $\ChirHoch^*(\cA,\cA)$ is $\Etwo$-formal over the KZ model.
\item $U_6$ \emph{(curve independence):} the bar complex of
 $\cA$ is independent of the curve~$X$ within the
 Deligne--Mumford stratum of~$\cA$.
\item $U_7$ \emph{(PBW universality):}
 the associated graded $R_\cA = \gr^F\!\cA$ is a
 polynomial Poisson vertex algebra under~$F_\bullet$, and the
 PBW deformation is flat on the finite comparison window. This
 is the PBW-free chart: freely strongly generated vertex
 algebras satisfy it, but simple quotients and logarithmic
 orbifold or triplet examples do not inherit it merely from their
 ambient algebra.
\item $U_8$ \emph{(Barr--Beck--Lurie monadicity):}
 $\cA \mapsto \barBch(\cA)$ is monadic over the category of
 counital conilpotent factorisation coalgebras.
\item $U_9$ \emph{(factorisation homology concentration):}
 $\int_X \cA$ is concentrated in the expected factorisation
 degree (uniform-weight~$g=0$; $g\geq 1$
 scalar-lane, Remark~\ref{v1-rem:kms-uniform-weight-tag}).
\item $U_{10}$ \emph{(FM boundary acyclicity):} the pullback of
 $\barBch(\cA)$ to the boundary strata of $\FM_n(X)$ is
 acyclic in degrees $\geq 2$.
\end{enumerate}

\smallskip
\noindent\textup{(} \emph{Home coordinate}
$\Phi_{\mathrm{AT}}$, chart $U_{11}$\textup{):}
\begin{enumerate}[label=\textup{(\roman*)},resume,leftmargin=2.4em]
\item $U_{11}$ \emph{(Lagrangian criterion at
 Alekseev--Torossian):} the derived intersection of
 $\cM_\cA$ and $\cM_{\cA^!}$ inside
 $\cM^{\mathrm{AT}}_{\mathrm{comp}}$ has acyclic tangent fibre
 $\mathbb T^{\mathrm{AT}}_{\mathrm{int}}$.
\end{enumerate}

\smallskip
\noindent\textup{(} \emph{Home coordinate}
$\Phi_{\mathrm{dR,B}}$, chart $U_{12}$\textup{):}
\begin{enumerate}[label=\textup{(\roman*)},resume,leftmargin=2.4em]
\item $U_{12}$ \emph{(mixed Hodge module purity):}
 the Hodge--Betti finite-resolution hypotheses hold and each
 $\barBch_n(\cA)$ is pure of weight $n$ as a mixed Hodge module.
\end{enumerate}

\smallskip
\noindent\textup{(} \emph{Home coordinate}
$\Phi_{\mathrm{ell}}$, chart $U_{13}$\textup{):}
\begin{enumerate}[label=\textup{(\roman*)},resume,leftmargin=2.4em]
\item $U_{13}$ \emph{(genus-one twisted K\"unneth):}
 $\barBch(\cA \boxtimes_{\mathrm{ell}} \cA^!) \simeq
 \barBch(\cA) \boxtimes_{\mathrm{ell}} \barBch(\cA^!)$
 on $\overline{\cM}_{1,n}$.
\end{enumerate}

\smallskip
\noindent\textup{(} \emph{Home coordinate}
$\Phi_{\mathrm{Kon}}$, chart $U_{14}$\textup{):}
\begin{enumerate}[label=\textup{(\roman*)},resume,leftmargin=2.4em]
\item $U_{14}$ \emph{(Swiss-cheese homotopy-Koszulity):}
 the Kontsevich comparison complex for the action of
 $\SCchtop$ on the pair
 $(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA),\cA)$ is
 homotopy-Koszul at every Maurer--Cartan degree.
\end{enumerate}

On an admissible home chart each of $U_1,\ldots,U_{14}$ is
equivalent to completed chiral Koszulness. The KZ-scoped split is
the restriction of the completed atlas to the KZ coordinate.
\end{theorem}

\begin{proof}
Charts $U_1$--$U_{10}$ are established at $\Phi_{\mathrm{KZ}}$
by the comparison maps supplied in
Chapters~\ref{chap:koszul-pair-structure} and
\ref{chap:bar-cobar-adjunction} of this volume
(bar--cobar adjunction, PBW filtration, and the finite-stage
existence loci and obstruction classes of
Propositions~\ref{prop:existence-four-loci} and
\ref{prop:finite-stage-obstruction-classes}). Each of
these is stated natively in the KZ language (PBW spectral
sequence, bar cohomology concentration, $\Ainfty$-formality,
etc.) and computes the KZ finite Koszul cone under its stated
PBW and finiteness hypotheses.

The four supplementary charts are the content of
Propositions~\ref{v1-prop:kms-at-chart},
\ref{v1-prop:kms-hodge-betti-chart},
\ref{v1-prop:kms-elliptic-chart}, and
\ref{v1-prop:kms-kontsevich-chart} below, each proved at its
own associator. Equivalence on each home chart is the content of
those propositions.

Equivalence across admissible charts is
Theorem~\ref{v1-thm:kms-moduli}\ref{v1-item:kms-A3}: any two
admissible charts $U_j$ and $U_k$ are connected by a Tamarkin
transfer path $g_{jk}\colon \Phi_j \leadsto \Phi_k$ that
preserves the Koszul cone up to filtered quasi-isomorphism.
Equivalence is therefore a chart-local property, under the finite
PBW--Artin hypotheses above, coherent across the atlas. A
predicate without its comparison quasi-isomorphism is not counted
as a chart equivalence.
\end{proof}

\begin{remark}[Scope of the PBW-universality chart]
\label{v1-rem:kms-pbw-universality-scope}
Chart $U_7$ is a sufficient PBW-free test on its admissible home
component, not a global converse to chiral Koszulness. Free strong
generation supplies the test, as in
Proposition~\ref{prop:pbw-universality}. Outside that component,
for example for simple quotients with null-vector ideals and for
logarithmic triplet or orbifold constructions, the atlas requires a
separate bar, determinant, or comparison-complex argument before
$U_7$ can be used as an equivalence.
\end{remark}

\begin{remark}[Scope of the uniform-weight tag]
\label{v1-rem:kms-uniform-weight-tag}
Chart $U_9$ (factorisation homology concentration) refers to
the scalar-channel uniform-weight regime at genus
$g\geq 1$: the scalar coefficient $\kappa_{\mathrm{ch}}(\cA)$
controls a single universal Maurer--Cartan
datum, and multi-weight corrections
$\delta F_g^{\mathrm{cross}}$ are tracked separately
(Theorem~\ref{thm:multi-weight-genus-expansion}). At
$g=0$ and at the uniform-weight scalar lane for $g\geq 1$,
$U_9$ is a KZ chart test; the full
all-weight strengthening lives on the Lagrangian chart
$U_{11}$ at $\Phi_{\mathrm{AT}}$.
\end{remark}

% =====================================
\subsection{Chart $U_{11}$: Alekseev--Torossian}
% =====================================

\begin{proposition}[Alekseev--Torossian chart]
\label{v1-prop:kms-at-chart}
\ClaimStatusProvedHere
At the Alekseev--Torossian associator $\Phi_{\mathrm{AT}}$
\cite{AT12}, fix the finite PBW comparison component on which
the Kashiwara--Vergne tangent complex is perfect. Let
\[
\cM_\cA,\ \cM_{\cA^!}\longrightarrow
\cM^{\mathrm{AT}}_{\mathrm{comp}}
\]
be the two derived formal moduli maps defined by~$\cA$ and by
the Verdier dual algebra
$\cA^!=(H^\bullet(\barBch(\cA)))^\vee$. At a point~$x$ of their
derived intersection, set
\[
\mathbb T^{\mathrm{AT}}_{\mathrm{int},x}
=
\operatorname{fib}\!\left(
\mathbb T_x\cM_\cA\oplus \mathbb T_x\cM_{\cA^!}
\longrightarrow
\mathbb T_x\cM^{\mathrm{AT}}_{\mathrm{comp}}
\right).
\]
On this component, chiral Koszulness of~$\cA$ is equivalent to
AT Lagrangian transversality, meaning
$\mathbb T^{\mathrm{AT}}_{\mathrm{int},x}\simeq 0$, and hence to
acyclicity of the AT-twisted Koszul cone. The statement is
finite-type and chart-local; it does not assert perfectness of
the whole KZ deformation ambient.
\end{proposition}

\begin{proof}
The Alekseev--Torossian associator is constructed from the
Kashiwara--Vergne equations on free Lie algebras
\cite{AT12}: it provides an explicit homotopy between the KZ
associator and its symmetrisation, together with a canonical
choice of Baker--Campbell--Hausdorff basis. Transport the
$(-1)$-shifted symplectic deformation space
$\cM_{\mathrm{comp}}$ of the classical Lagrangian criterion
to $\cM^{\mathrm{AT}}_{\mathrm{comp}}$ using the AT gauge:
\[
\Psi_{\mathrm{AT}}\colon
\cM_{\mathrm{comp}} \xrightarrow{\;\sim\;}
\cM^{\mathrm{AT}}_{\mathrm{comp}},
\qquad
\Psi_{\mathrm{AT}}^*\omega_{\mathrm{AT}} = \omega.
\]
By definition of the finite AT component, the ambient tangent
complex of $\cM^{\mathrm{AT}}_{\mathrm{comp}}$ is the perfect
two-term Kashiwara--Vergne complex: its generators are the
KV pair $(F,H)$ and its relations are the
Duflo--Kontsevich equations. The maps
$\cM_\cA\to\cM^{\mathrm{AT}}_{\mathrm{comp}}$ and
$\cM_{\cA^!}\to\cM^{\mathrm{AT}}_{\mathrm{comp}}$ are induced by
the AT-twisted convolution dg Lie algebras of~$\cA$ and of the
Verdier dual~$\cA^!$. The tangent complex of their derived
intersection is the displayed homotopy fibre. Its vanishing is
derived transversality.

The same fibre computes the obstruction complex of the
AT-twisted Koszul cone:
\[
\mathbb T^{\mathrm{AT}}_{\mathrm{int},x}
\simeq
\operatorname{Cone}\bigl(
K_\tau^{\mathrm{AT}}(\cA,\cA^!)\to 0
\bigr)[-1].
\]
Thus transversality is equivalent to acyclicity of
$K_\tau^{\mathrm{AT}}(\cA,\cA^!)$. The AT-twisted product is
quasi-isomorphic to the KZ-twisted product by the Tamarkin
transfer along the $\mathrm{GRT}_1$ path from
$\Phi_{\mathrm{KZ}}$ to $\Phi_{\mathrm{AT}}$; by
Theorem~\ref{v1-thm:kms-moduli}\ref{v1-item:kms-A1}, this
acyclicity is chiral Koszulness of~$\cA$.
\end{proof}

\begin{remark}[Perfectness as chart coordinate]
\label{v1-rem:kms-perfectness-internal}
The Lagrangian criterion carries a perfectness hypothesis which
is not generally verifiable
from the input $\cA$. On the AT chart this hypothesis is
not a separate axiom: it is part of the chart coordinate
(the Duflo--Kontsevich relations built into
$\cM^{\mathrm{AT}}_{\mathrm{comp}}$). Moving to the AT coordinate
restricts the test to the finite comparison component whose
tangent complex is perfect; it does not assert that the whole KZ
deformation ambient becomes perfect after a gauge change.
\end{remark}

% =====================================
\subsection{Chart $U_{12}$: de Rham--Betti}
% =====================================

\begin{proposition}[Hodge--Betti chart]
\label{v1-prop:kms-hodge-betti-chart}
\ClaimStatusProvedHere
At the de Rham--Betti associator $\Phi_{\mathrm{dR,B}}$
\cite{Deligne89}, let $\cA$ be of finite PBW type with
conformal-weight grading and a strict mixed-Hodge PBW
resolution of the unit. Then the finite-stage purity locus
\[
\barBch_n(\cA)\text{ pure of weight }n,\qquad n\le N,
\]
is a closed Hodge-theoretic sublocus, the finite-stage
Koszul locus is open, and on the strict pure-resolution
component the two completed loci coincide. Thus, on this
component, chiral Koszulness is equivalent to mixed-Hodge
purity of the bar pieces.
\end{proposition}

\begin{proof}
The de Rham--Betti associator sits at the boundary point of the
Drinfeld associator torsor where the KZ connection on
$\FM_n(\bC)$ is identified with the comparison isomorphism
between de Rham and Betti cohomology of a mixed Hodge
structure \cite{Deligne89}. At this base point, chart
coordinates are weight-filtered mixed Hodge structures on the
bar complex.

For $\cA$ with strict mixed-Hodge PBW filtration, the
Hodge--Betti chart detects purity directly: the weight
filtration on $\barBch_n(\cA)$ is recovered from the
Hodge--Betti period matrix, and purity is the vanishing of the
off-weight graded pieces. At finite PBW stage these vanishings
are closed determinantal conditions. Koszulness is acyclicity of
the finite cone $C_{\Phi_{\mathrm{dR,B}},N}$ and is open by the
Fitting-ideal criterion in
Theorem~\ref{v1-thm:kms-moduli}.

On the strict pure-resolution component the weight spectral
sequence degenerates for weight reasons. Purity then kills all
off-diagonal bar cohomology, hence the finite Koszul cone is
acyclic at every stage. Conversely, acyclicity of the Koszul
cone forces the same off-weight graded pieces to vanish because
the resolution is strict. The generic Virasoro component is
closed by the Feigin--Fuchs argument of
Theorem~\ref{v1-thm:kms-virasoro-noncircular}; for simple
$\cW$-algebras the same strict-resolution hypothesis is supplied
by Drinfeld--Sokolov reduction with parabolic screenings
\cite{KRW03,Arakawa07}. Outside the strict pure-resolution
component this proposition asserts the closed purity locus and
the open Koszul locus, not their equality.
\end{proof}

% =====================================
\subsection{Chart $U_{13}$: Enriquez elliptic}
% =====================================

\begin{proposition}[Enriquez elliptic chart]
\label{v1-prop:kms-elliptic-chart}
\ClaimStatusProvedHere
At the Enriquez elliptic associator $\Phi_{\mathrm{ell}}$
\cite{Enriquez14}, let $\cA$ be of finite PBW type and suppose
the elliptic KZB comparison complex is perfect at every finite
stage and compatible with PBW completion. On this elliptic
comparison component, chiral Koszulness of~$\cA$ is equivalent
to flatness of the genus-one twisted K\"unneth formula
\[
\barBch(\cA \boxtimes_{\mathrm{ell}} \cA^!)
\;\simeq\;
\barBch(\cA) \boxtimes_{\mathrm{ell}} \barBch(\cA^!)
\]
on the elliptic configuration space
$\overline{\cM}_{1,n}$.
The chart is a genus-one home-coordinate equivalence on this
component; it distinguishes the class~$\mathrm{L}$ stratum by
direct computation.
\end{proposition}

\begin{proof}
The Enriquez elliptic associator \cite{Enriquez14} is
constructed from the KZB connection on the universal elliptic
curve; it provides a canonical elliptic completion of the KZ
associator with $\mathrm{SL}_2(\bZ)$-equivariance built in.
The chart coordinate at $\Phi_{\mathrm{ell}}$ is the elliptic
twisted K\"unneth isomorphism: for chirally Koszul~$\cA$, the
genus-one bar complex factorises as a K\"unneth product of
genus-zero data twisted by the elliptic R-matrix.

On the elliptic comparison component, flatness of the twisted
K\"unneth is equivalent to
$\Etwo$-collapse of the genus-one PBW spectral sequence on the
elliptic curve. This is condition~$U_1$ transported to
$\FM_n(E)$; the classical proof on $\FM_n(\bC)$ carries over,
using the fact that the elliptic R-matrix (Felder 1994) is the
image of the rational R-matrix under the Tamarkin transfer
from $\Phi_{\mathrm{KZ}}$ to $\Phi_{\mathrm{ell}}$.
Coassociativity uses the Fay trisecant identity for theta
functions (not the Drinfeld pentagon; the pentagon is a
genus-zero identity and the elliptic coassociativity is a
genus-one identity).
Hence $U_{13}$ is witnessed on its home chart; it
distinguishes class~$\mathrm{L}$ because affine
Kac--Moody algebras at generic level are where the cubic
bracket~$S_3$ on the shadow algebra first activates, as computed in
the affine cubic normal form
\textup{(}Theorem~\ref{thm:affine-cubic-normal-form}\textup{)}.
\end{proof}

% =====================================
\subsection{Chart $U_{14}$: Kontsevich integral}
% =====================================

\begin{proposition}[Kontsevich integral chart]
\label{v1-prop:kms-kontsevich-chart}
\ClaimStatusProvedHere
At the Kontsevich integral associator $\Phi_{\mathrm{Kon}}$
\cite{Kontsevich93}, assume the derived-centre pair
$(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA),\cA)$ carries a
weight-complete $\SCchtop$ action and that the Kontsevich
chord-diagram comparison complex maps by filtered
quasi-isomorphisms to the finite Koszul cones. On this
comparison component, chiral Koszulness of~$\cA$ is equivalent
to homotopy-Koszulity of that $\SCchtop$ comparison complex at
every degree of the Maurer--Cartan expansion. On the
class~$\mathrm{M}$ stratum the Kontsevich integral provides the
home coordinates for the infinite shadow tower; convergence in
the weight-completed coderived category is part of the chart
hypothesis.
\end{proposition}

\begin{proof}
The Kontsevich integral \cite{Kontsevich93} is the universal
Vassiliev invariant: it assembles into an associator
$\Phi_{\mathrm{Kon}}$ at the Vassiliev base point with chart
coordinates indexed by chord diagrams. For chirally Koszul~$\cA$,
the Maurer--Cartan element $\Theta_\cA$ is a sum over chord
diagrams in the Kontsevich expansion, each coefficient
computed by a shadow algebra bracket.

Homotopy-Koszulity of the $\SCchtop$ comparison complex acting on the pair
$(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA),\cA)$ is the condition
that the bar complex of $\SCchtop$ has cohomology
concentrated on the operadic diagonal. At the Kontsevich base
point, this is the assertion that chord-diagram coefficients
satisfy the IHX and STU relations. The cohomological part is
the formality input for the two-coloured little-disks operad
\textup{(}Proposition~\ref{prop:en-formality}, applied
cohomologically; a chain-level $\SCchtop$-formality claim is
not asserted here, consistent with the chain-level vs rational
distinction for formality-based E-structure lifts\textup{)}.
Note that $\SCchtop$ is the correct operad acting on the
\emph{pair} $(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA),\cA)$:
$\barBch(\cA)$ itself is an $\Eone$-chiral coassociative
coalgebra, not a Swiss-cheese coalgebra
(Remark~\ref{v1-rem:kms-native-vs-derived-en}).

On class~$\mathrm{M}$ (Virasoro, $\cW_N$), the chart is
the Kontsevich coordinate for the infinite shadow tower:
$S_2,S_3,S_4,\ldots$ supply the coefficients of the
Kontsevich expansion, and the chart predicate is convergence of
this expansion in the weight-completed coderived category specified
by the chart hypothesis.
\end{proof}

\begin{remark}[Chart redundancy and the torsor structure]
\label{v1-rem:kms-chart-redundancy}
The fourteen charts are redundant only after admissibility is
fixed: any one whose comparison complex computes the Koszul cone
detects chiral Koszulness. Theorem~\ref{v1-thm:kms-moduli}\ref{v1-item:kms-A3}
asserts that the framed redundancy is organised over the
associator torsor, and
Theorem~\ref{v1-thm:kms-moduli}\ref{v1-item:kms-A5} asserts
that the redundancy is broken on each stratum by a
distinguished chart. The redundancy is coherent, not wasteful:
each chart is best adapted to a stratum. The number fourteen is
the size of the selected classical test list, not a finiteness
theorem for the pro-unipotent group $\mathrm{GRT}_1$.
\end{remark}

\begin{theorem}[Koszulness is $\mathrm{GRT}_1$-invariant;
admissible characterisations are charts]
\label{v1-thm:kms-koszulness-is-grt-invariant}
\ClaimStatusProvedHere
Chiral Koszulness is a $\mathrm{GRT}_1$-invariant property of
a chiral algebra. Every admissible classical characterisation is
a $\mathrm{GRT}_1$-coordinate chart: its test complex is
identified with the Koszul cone, and the Kontsevich--Tamarkin
transfer \cite{Kontsevich99,Tamarkin03} transports the
comparison quasi-isomorphism across associator coordinates.
\end{theorem}

\begin{proof}
Combine
Theorem~\ref{v1-thm:kms-moduli}\ref{v1-item:kms-A1}--\ref{v1-item:kms-A4}
and Corollary~\ref{v1-cor:kms-grt-invariant}. Invariance of the
property is~\ref{v1-item:kms-A1}; chart structure
is~\ref{v1-item:kms-A4}; the transfer is the torsor
action~\ref{v1-item:kms-A3}.
\end{proof}

% ================================================================
\section{Frontier closures: Virasoro and Yangian}
\label{v1-sec:kms-frontier-closures}
% ================================================================

\subsection{Virasoro non-circular closure}

The classical proof of Virasoro Koszulness at generic~$c$
traced a bar--cobar circle: Koszulness implies
$\Etwo$-collapse, which implies concentration of chiral
Hochschild cohomology, with the converse closing the loop
through bar--cobar inversion. Every step uses the bar complex;
the circularity is latent. The
Hodge--Betti chart $U_{12}$ provides an independent proof via
Feigin--Fuchs BGG resolution \cite{FeiginFuchs90,RCW82}.

\begin{theorem}[Virasoro Koszulness, non-circular]
\label{v1-thm:kms-virasoro-noncircular}
\ClaimStatusProvedHere
For the Virasoro vertex algebra $\Vir_c$ at generic central
charge $c \notin \{c_{p,q} : (p,q) \in \bZ^2_{>0},
\gcd(p,q)=1\}$, the bar cohomology satisfies
\[
H^\bullet(\Vir_c,\Vir_c)_{\mathrm{weight}\,r+1} = 0
\qquad \text{for all } r \geq 2,
\]
without appeal to bar--cobar inversion. Consequently,
$\Vir_c$ is chirally Koszul, proved directly at the $U_{12}$
chart.
\end{theorem}

\begin{proof}
We work entirely at the Hodge--Betti chart $U_{12}$. The proof
has four steps.

\emph{Step 1: Feigin--Fuchs BGG resolution.}
For each highest weight~$h$ in the vacuum Verma module
$M_0(c)$ of $\Vir_c$, the Feigin--Fuchs theorem
\cite{FeiginFuchs90} (see also Rocha-Caridi--Wallach
\cite{RCW82}) constructs a resolution of the vacuum irreducible
by Verma modules indexed by elements of an affine Weyl group
acting on weights:
\[
\cdots \to
\bigoplus_{w \in W^{(2)}} M_{w\cdot 0}(c) \to
\bigoplus_{w \in W^{(1)}} M_{w\cdot 0}(c) \to
M_0(c) \to L(c,0) \to 0,
\]
with differentials given by singular-vector embeddings. At
generic~$c$ (outside the minimal-model lattice), each
singular-vector embedding is nonzero and the resolution is
exact. Each term is a Verma module, whose mixed Hodge
structure is pure of weight given by its conformal weight
(Verma modules have free PBW associated graded).

\emph{Step 2: Kac determinant non-degeneracy.}
The Kac determinant at conformal weight~$h$ is
\[
\det G_h
\;=\;
\prod_{\substack{p,q \geq 1 \\ pq \leq h}}
(h - h_{p,q}(c))^{P(h - pq)},
\]
where $P$ is the partition function and
$h_{p,q}(c) =
 ((p\alpha_+ + q\alpha_-)^2 - (\alpha_+ + \alpha_-)^2)/4$
with $\alpha_\pm$ the Liouville parameters determined by~$c$
\cite{KacBook,FeiginFuchs90}. For~$c$ outside the
minimal-model lattice, $\det G_h \neq 0$ at every
bar-relevant weight~$h$: the BGG resolution of Step~1 embeds
faithfully in the bar complex.

\emph{Step 3: Purity of the bar complex.}
Combine Steps~1 and~2. The BGG resolution gives a
$\cD$-module resolution of the unit $\omega_X$ of $\Vir_c$ by
a sum of Verma modules; each Verma module is pure of its
conformal weight in the Hodge--Betti category. Kac
non-degeneracy at generic~$c$ guarantees that the BGG
differentials are injective at every weight, so the resolution
is exact. The bar complex $\barBch_n(\Vir_c)$ is
quasi-isomorphic to the $n$-fold iterate of this resolution,
and iterated pure objects remain pure by Saito's stability
theorem \cite{Saito}.

\emph{Step 4: Weight vanishing.}
Purity of $\barBch_n(\Vir_c)$ of weight~$n$ forces
$H^\bullet(\Vir_c,\Vir_c)_{\mathrm{weight}\,r+1} = 0$ for
every $r \geq 2$ off the Koszul diagonal: any nonzero class
in weight $r+1 \neq n$ would contradict purity.

\emph{Conclusion.}
The four steps use Feigin--Fuchs BGG (Step~1), Kac
determinant (Step~2), Saito stability (Step~3), and purity
vanishing (Step~4). No bar--cobar inversion is invoked; the
circularity of the classical proof path is closed at the $U_{12}$
chart.
\end{proof}

\begin{remark}[Why this closes the classical circularity]
\label{v1-rem:kms-fm197-closed}
The circular Virasoro route uses bar--cobar inversion in its
final step, then claims Koszulness, which entails bar--cobar
inversion, as a consequence. The Hodge--Betti chart resolves this
because purity is checked against a resolution (BGG) and a
determinant (Kac) that exist independently of the bar
complex: the chiral bar complex is a \emph{consumer} of the
BGG--Kac data in this proof, not a \emph{producer}, and the
logical arrow goes Feigin--Fuchs~$\to$~bar, never
bar~$\to$~bar. The circular proof routing is discharged
on the Virasoro branch.
\end{remark}

\subsection{Yangian chart inclusion}

The associative Koszulness of the Yangian $Y_\hbar(\fg)$
for~$\fg$ simple uses the Polishchuk--Positselski nonhomogeneous
Koszul framework \cite{Positselski11}. The chiral question is
whether this Koszulness upgrades to the chiral setting. The
moduli reformulation phrases this as a chart inclusion.

\begin{theorem}[Yangian chart inclusion]
\label{v1-thm:kms-yangian-embedding}
\ClaimStatusConditional
For the Yangian $Y_\hbar(\fg)$ with~$\fg$ simple, assume that the
evaluation-module construction gives a finite-PBW $\Eone$-chiral
avatar and that the associative-to-chiral chart functor is
representable and reflects the Shapovalov open locus. Then the framed
finite PBW associative Koszulness moduli embeds as a
$\mathrm{GRT}_1$-equivariant open subfunctor of the framed
finite-stage chiral Koszulness moduli:
\[
\cM^{\mathrm{assoc}}_{\mathrm{Kosz}}(Y_\hbar)
\;\hookrightarrow\;
\cM^{\mathrm{chiral}}_{\mathrm{Kosz}}(Y_\hbar).
\]
At a fixed finite PBW stage and gauge framing this map is an
open immersion of affine schemes. In the completed unframed
setting it is the induced morphism of derived quotient stacks,
provided the PBW tower is Mittag--Leffler. The honest open
question is chart-surjectivity: whether every chiral chart lifts
a classical associative chart.
The statement is the comparison theorem under these hypotheses; it is
not a construction of the missing higher-rank chiral atlas.
\end{theorem}

\begin{proof}
For $\Phi = \Phi_{\mathrm{KZ}}$, the associative PBW chart
$U_1^{\mathrm{assoc}}$ detects $Y_\hbar(\fg)$-Koszulness in
the classical Polishchuk--Positselski sense
\cite{Positselski11}, framed as a filtered-CDG-Koszul
deformation of $U(\fg[t])$ with level-filtration-compatible
nonhomogeneous relations. For all simple Lie algebras
(classical types via Molev's PBW \cite{Molev2007}; exceptional
types $E_6, E_7, E_8, F_4, G_2$ via Guay--Regelskis--Wendlandt
\cite{GRW18}) this chart is nonempty.

Transport the associative chart coordinate to the chiral
setting through the assumed finite-PBW $\Eone$-chiral avatar
(Definition~\ref{def:yangian-e1-chiral},
Chapter~\ref{ch:ordered-associative-chiral-kd}). The RTT data
then defines the required formal-disk chiral structure through the
evaluation modules~$V_u$, and the PBW filtration is compatible with the
chiral bracket. The associative chart coordinate
$(\Phi_{\mathrm{KZ}}, c^{\mathrm{assoc}}_{\mathrm{KZ}})$ maps
to the chiral chart coordinate
$(\Phi_{\mathrm{KZ}}, c^{\mathrm{chiral}}_{\mathrm{KZ}})$:
both detect $\Etwo$-collapse of the same PBW spectral
sequence, the associative one on $Y_\hbar(\fg)$ and the
chiral one on its $\Eone$-chiral avatar. Hence
$\cM^{\mathrm{assoc}}_{\mathrm{Kosz}}(Y_\hbar)
\hookrightarrow
\cM^{\mathrm{chiral}}_{\mathrm{Kosz}}(Y_\hbar)$
is defined on framed finite PBW stages and is
$\mathrm{GRT}_1$-equivariant.

By the open-locus hypothesis, the associative chart
$U_1^{\mathrm{assoc}}$ is the complement of the zero locus of the
Shapovalov determinant, and its preimage in
$\cM^{\mathrm{chiral}}_{\mathrm{Kosz}}(Y_\hbar)$ is the
complement of the same zero locus, hence open. Passing to the
completed unframed object is legitimate only under the
Mittag--Leffler and PBW--Artin hypotheses stated in
Theorem~\ref{v1-thm:kms-moduli}.
\end{proof}

\begin{corollary}[Exceptional-type Yangian PBW input via GRW18]
\label{v1-cor:kms-exceptional-PBW}
\ClaimStatusProvedElsewhere
Via Guay--Regelskis--Wendlandt \cite{GRW18}, the Yangians
$Y_\hbar(E_6)$, $Y_\hbar(E_7)$, $Y_\hbar(E_8)$,
$Y_\hbar(F_4)$, $Y_\hbar(G_2)$ admit PBW bases, closing the
exceptional-type PBW input for the finite-stage comparison. This does
not construct an exceptional finite RTT/FRT packet, nor does it prove
the chiral chart immersion without the finite-PBW avatar and open-locus
hypotheses.
\end{corollary}

\begin{remark}[Associative versus chiral atlas for Yangians]
\label{v1-rem:kms-fm161-closed}
The associative and chiral Koszulness atlases for Yangians do
not coincide by formal necessity. The moduli reformulation makes
the gap precise at framed finite PBW stage: the associative atlas
is an open subfunctor of the chiral atlas. The honest open
question is whether the embedding is \emph{surjective}: whether
every chiral chart lifts an associative one, or whether there
exist genuinely chiral charts with no associative avatar. For
$\fg = \mathfrak{sl}_2$ the embedding is an isomorphism (the
Yangian has no genuinely chiral Koszul data beyond the
associative PBW, Theorem~\ref{thm:sl2-yangian-triangle-concrete});
for higher rank, chart-surjectivity is open and is the
correct form of the associative--chiral comparison question.
\end{remark}

% ================================================================
\section{Meta-Koszulness: the moduli as a Koszul object}
\label{v1-sec:kms-meta}
% ================================================================

The Koszulness moduli object carries a natural
$\mathrm{GRT}_1$-action on framed admissible charts by
\ref{v1-item:kms-A3}. This action promotes the tangent category
of the finite-stage chart stack to an $\Etwo$-object. The
completed statement is the compatible inverse limit of these
finite-stage actions, not a claim that the unframed pro-object is
an affine scheme.

\begin{theorem}[Meta-Koszulness]
\label{v1-thm:kms-meta-koszulness}
\ClaimStatusProvedHere
Fix a finite PBW--Artin stage~$(N,m)$ and a gauge framing. The
tangent dg category of admissible chart coordinates in
$\cM_{\mathrm{Kosz}}^{N,m}(\cA)$ carries a natural
$\Etwo$-structure. The bracket is induced by the finite quotient
$\mathfrak{grt}_{1,\le m}$ acting by derivations on chart
coordinates: for compatible admissible charts $(U_j,U_k)$, the
infinitesimal transfer
$\delta_{jk}\in\mathfrak{grt}_{1,\le m}$ defines a degree-zero
operation
$\{-,-\}^{\Etwo}\colon
 \mathrm{T}_{U_j}\cM_{\mathrm{Kosz}}(\cA)
 \otimes \mathrm{T}_{U_k}\cM_{\mathrm{Kosz}}(\cA)
 \to \mathrm{T}_{U_{jk}}\cM_{\mathrm{Kosz}}(\cA)$
that satisfies the $\Etwo$ relations. If the PBW tower is
derived Mittag--Leffler, these finite-stage structures assemble
to a pro-$\Etwo$-structure on the completed tangent category.
Consequently, whenever the Hochschild derived centre of this
finite-stage $\Etwo$-category is defined, it is an $E_3$-algebra
by Deligne.
\end{theorem}

\begin{proof}
The Grothendieck--Teichm\"uller group $\mathrm{GRT}_1$ is
pro-unipotent with Lie algebra $\mathfrak{grt}_1$. By
Willwacher \cite{Willwacher15}, $\mathfrak{grt}_1$ is the
degree-zero part of the graph cohomology of Kontsevich,
which carries a canonical $\Etwo$-structure by
Kontsevich--Tamarkin formality. At finite quotient~$m$, this
gives the action of $\mathfrak{grt}_{1,\le m}$ on admissible
chart transitions. The comparison quasi-isomorphisms in
Definition~\ref{v1-def:kms-moduli-scheme} identify the tangent
directions of the charts with tangent directions of the finite
Koszul cone, so the bracket descends to the tangent dg category
of $\cM_{\mathrm{Kosz}}^{N,m}(\cA)$. The Tamarkin cocycle
condition gives the $\Etwo$ relations on triple overlaps.

The derived Mittag--Leffler hypothesis lets these finite-stage
brackets pass to the PBW completion without hidden
$\mathbf R^1\!\varprojlim$ terms. Deligne's Hochschild
cohomology theorem then gives an $E_3$-structure on the derived
centre of the resulting finite-stage $\Etwo$-category. The
$E_3$-object is the derived centre of the moduli category, not
$\cA$, not $\barBch(\cA)$, and not $\cA^!$; this is the
five-object firewall of
Remark~\ref{v1-rem:kms-native-vs-derived-en}. The derived centre
is a right-adjoint construction, not an averaging.
\end{proof}

\begin{remark}[Meta-Koszulness and the chart count]
\label{v1-rem:kms-fm198-closed}
The KZ-coordinate count overstates the generic-parameter
standard landscape. The honest count there is seven
intrinsic bidirectional equivalences plus a
Barr--Beck--Lurie restatement, a Theorem~H-conditional chiral
Hochschild consequence, a perfectness-conditional Lagrangian criterion, and
a one-directional $\mathcal{D}$-module purity implication. The
meta-Koszulness theorem gives the correct carrier: each
admissible classical condition is a chart on a derived atlas, and
the finite-stage tangent category of that atlas carries an
$\Etwo$-structure. Counting by home associator produces the
10~KZ $+$ 1~AT $+$ 1~dR,B $+$ 1~ell $+$ 1~Kon $=$ 14 chart
decomposition of
Theorem~\ref{v1-thm:kms-fourteen-unconditional}.
\end{remark}

\begin{remark}[Functor of points]
\label{v1-rem:kms-construction-not-narration}
The moduli object $\cM_{\mathrm{Kosz}}(\cA)$ is constructed as
the derived functor of points
$(\Phi,\xi,h_\xi)$ in Definition~\ref{v1-def:kms-moduli-scheme}.
The finite PBW truncations are classical schemes only after
framing and under the perfect finite-type hypotheses of
Theorem~\ref{v1-thm:kms-moduli}. The Kontsevich--Tamarkin
transfer provides the operadic input.
\end{remark}

% ================================================================
\section{Consequences of the Koszulness moduli object}
\label{v1-sec:kms-summary}
% ================================================================

The Koszulness moduli object replaces a flat list of
fourteen equivalent-in-name Koszulness criteria by a single
derived deformation problem whose points are associator
coordinates, twisting deformations, and null-homotopies of the
Koszul cone. The construction has three formal consequences.

First, the seven-core-plus-satellites split of the
KZ presentation (seven intrinsic bidirectional equivalences;
Barr--Beck--Lurie as a listed consequence; conditional
factorization homology; Theorem~H-conditional chiral Hochschild consequence;
conditional Lagrangian criterion; one-directional
$\mathcal{D}$-module purity) resolves as a KZ-coordinate restriction:
on its admissible home chart each of the fourteen
characterisations is equivalent to completed chiral Koszulness
(Theorem~\ref{v1-thm:kms-fourteen-unconditional}).

Second, Virasoro Koszulness at generic central charge admits
a non-circular proof at the Hodge--Betti chart via
Feigin--Fuchs BGG resolution
(Theorem~\ref{v1-thm:kms-virasoro-noncircular}), discharging
the classical circularity on the Virasoro branch.

Third, the associative Koszulness atlas of the Yangian
$Y_\hbar(\fg)$ embeds as an open subfunctor of the framed
finite-stage chiral atlas
(Theorem~\ref{v1-thm:kms-yangian-embedding});
Guay--Regelskis--Wendlandt \cite{GRW18}
discharges exceptional-type PBW.

Beyond the closures, the moduli reformulation gives an
operational form of the Kontsevich--Tamarkin theorem:
chiral Koszulness is a $\mathrm{GRT}_1$-invariant property;
the admissible classical characterisations are
$\mathrm{GRT}_1$-coordinate charts; transitions between charts
are Tamarkin transfers; the completed tangent category carries a
pro-$\Etwo$-structure from
$\mathrm{GRT}_1$ (Theorem~\ref{v1-thm:kms-meta-koszulness}).
The 14-chart atlas is finite because it records the selected
classical test list; it is not an enumeration of associators in
the pro-unipotent torsor.

\begin{remark}[Reading the atlas as the Koszul Reflection orbit]
\label{v1-rem:kms-koszul-reflection-bridge}
\index{Koszul reflection!atlas as orbit of K-squared identity}
The fourteen admissible characterisations of
Theorem~\ref{v1-thm:kms-fourteen-unconditional} read the same
involutive structure $K^{2}\simeq\mathrm{id}$ of the Koszul
Reflection \textup{(}Theorem~\textup{\ref{thm:koszul-reflection}}\textup{)}
through fourteen $\mathrm{GRT}_1$-coordinate windows. The
shadow-class stratification
$\mathrm{G}\sqcup\mathrm{L}\sqcup\mathrm{C}\sqcup\mathrm{M}\sqcup\mathrm{FF}$
of property \ref{v1-item:kms-A5} is the partition of $\Kosz(X)$
by computational complexity of the bracket on the chiral derived
centre
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)=\ChirHoch^*(\cA,\cA)$;
the Climax (Chapter~\ref{chap:climax-platonic}) packages the
coordinate dependence into the universal Arnold connection and the
universal ghost functor (Chapter~\ref{chap:universal-conductor}).
The Koszulness moduli object is therefore the geometric witness
that the twelve listed conditions of
Theorem~\textup{\ref{thm:koszul-equivalences-meta}} (Chapter~\textup{\ref{chap:koszul-pairs}})
are not twelve parallel equivalences: seven form the intrinsic
bidirectional core, and the remaining five are consequences,
conditional criteria, or one-directional tests attached to
specific comparison hypotheses. The atlas records these
diagnostics for the single involution~$K$ without changing their
logical status.
\end{remark}

% Inherits preamble from Vol I main.tex; no new macros introduced.

\section{Synthesis}
\label{sec:kms-supplement}

\begin{remark}[Siegel-modular Koszul pair moduli]
\label{rem:kms-1}
The K3 base point has a Siegel modular comparison chart: the
Pasol--Zagier 2013 universal Igusa form $\Phi_{10}$ on
$\mathrm{Sp}_4(\mathbb Z)\backslash\mathbb H_2$ records the
denominator identity
$\prod(1-q^{r\alpha})^{c(r\alpha)}=\Phi_{10}$ for the
bar object $\barBch(\mathbf H_{\Delta_5})$ and the Verdier-dual
object $(\mathbf H_{\Delta_5})^!$. This Siegel quotient is not
the representing scheme for
$\cM_{\mathrm{Kosz}}(\mathbf H_{\Delta_5})$. It is a finite
Hodge-theoretic comparison locus on the K3 component; the
Humbert divisor $H_1\cup H_4$ is the discriminant of that
comparison, and
$[\Phi_{10}]\in H^2(\mathrm{Sp}_4(\mathbb Z)\backslash\mathbb H_2)$
is its Siegel modular class
\cite{PasolZagier2013,GritsenkoNikulin1998}.
\end{remark}

\begin{remark}[Moduli stratification by Humbert type]
\label{rem:kms-2}
The Siegel comparison locus stratifies by Humbert type. The
$H_1$-stratum, where a genus-$2$ curve splits as a product of
elliptic curves, hosts the bi-based Ran restriction to
$\mathrm{Ran}(E^{\mathrm{nod,sm}}_{24})$. The $H_4$-stratum
hosts the Kuga--Satake image of K3 surfaces with Picard rank
$\geq 17$ (Shioda--Mitani). The open complement hosts the
generic K3 Hodge structure. The monodromy of
$\mathcal L^{\Delta_5}$ around $H_1\cup H_4$ is the
Mukai--Humbert face of the $\mathbb Z/8$-class
$K^{\kappa_{\mathrm{ch}}}$ \cite{Bruinier2002,KugaSatake1967};
this is a Hodge-theoretic stratum of the K3 comparison chart,
not a stratification of the entire Koszulness moduli object.
\end{remark}

\section{K3 at the class-$\mathrm M$ stratum}
\label{sec:kms-supplement-ii}

\begin{remark}[K3 chart placement on the Koszulness moduli object;
\ClaimStatusProvedHere]
\label{rem:kms-K3-placement}
\index{K3!Koszulness moduli chart}
\index{Kontsevich associator!K3 home chart}
Under property~\ref{v1-item:kms-A5} of
Theorem~\ref{v1-thm:kms-moduli}, the shadow-class stratification of
$\cM_{\mathrm{Kosz}}(\mathbf H_{\Delta_5})$ places the K3 chiral
bialgebra on the class-$\mathrm M$ stratum
$\cM^{(\mathrm M)}_{\mathrm{Kosz}}(\mathbf H_{\Delta_5})$, with
distinguished home chart $U_{14}$ at $\Phi_{\mathrm{Kon}}$
(Kontsevich integral). Apply the class-$\mathrm M$ Riccati criterion
directly to the stress-tensor line of $\mathbf H_{\Delta_5}$ at
$c_{2d} = -214$: it has modular characteristic
$\kappa = c_{2d}/2 = -107$, cubic $\alpha = 2$, quartic
$S_4 = 5/112\,136$, and Riccati polynomial
$Q_{-214}(t) = (-214 + 6t)^2 + 80 t^2/(5\cdot(-214)+22)
= (6t - 214)^2 - 80 t^2/1048$ with nonvanishing Riccati
discriminant $\Delta_{\mathrm{Ricc}} = 40/(5c+22) = -5/131 \ne 0$,
so $Q_{-214}$ is irreducible, $r_{\max}=\infty$, and K3 falls on
the class-$\mathrm M$ Kontsevich chart. On the K3 base point, the
Kontsevich chart is admissible only after the
weight-complete $\SCchtop$ comparison complex for the
derived-centre pair
$(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\mathbf H_{\Delta_5}),
\mathbf H_{\Delta_5})$ is identified with the finite Koszul
cones as in Proposition~\ref{v1-prop:kms-kontsevich-chart}. The
chord-diagram expansion of the Kontsevich integral then admits
the $M_{24}$-equivariant refinement supplied by the
Cheng--Duncan--Harvey 2014 umbral-moonshine mock-modular
shadows.
\end{remark}

\begin{remark}[$\mathrm{GRT}_1$-transport of the K3 central charge;
\ClaimStatusProvedHere]
\label{rem:kms-grt-transport-312}
\index{$\mathrm{GRT}_1$-transport!K3 central charge}
\index{Grothendieck--Teichmüller!K3 chart transport}
The central charge
$c_{2d}(A_1,\Sigma_{0,24},\mathrm{all\ max})=-214$ is fixed by
the K3 algebra, not by an associator choice. The
Beem--Rastelli relation $c_{2d}/c_{4d}=-12$ is the integral of
the $6d$ anomaly polynomial
(Vol~II Remark~\ref{V2-rem:anomtop-anomaly-polynomial}), a
topological characteristic class on
$\mathrm K3\times\Sigma_{0,24}$. The
$\mathrm{GRT}_1$ action of
Theorem~\ref{v1-thm:kms-moduli}\ref{v1-item:kms-A3} changes the
chart presentation of the shadow tower, not the numerical
central charge: at
$\Phi_{\mathrm{KZ}}$ the shadow tower is read via PBW spectral
sequence ($S_2 = -107$, $S_4 = 5/112\,136$); at
$\Phi_{\mathrm{ell}}$ via KZB genus-one R-matrix (Felder 1994
elliptic R-matrix at modular parameter $\tau = i$); at
$\Phi_{\mathrm{Kon}}$ via chord-diagram expansion (the
umbral-moonshine shadow). All three readings give the same
number because they are chart presentations of the same
$\mathbf H_{\Delta_5}$ point.
\end{remark}

\begin{remark}[Humbert-$H_1$ monodromy as K3 chart-compatibility data;
\ClaimStatusProvedHere]
\label{rem:kms-humbert-cocycle}
\index{Humbert divisor!chart-transition cocycle}
\index{K3!triple face of $8$}
The triple-face identity
$K^{\kappa_{\mathrm{ch}}} = 2 c_+(\mathrm{Mukai}) = \mathrm{ord}(\mathrm{mon}\,H_1)
= \ell_{\mathrm{Lusztig}} = 8$ (the Vol~III
Humbert-monodromy computation) supplies a necessary
compatibility condition for K3 chart transitions. The holonomic
$\mathcal D$-module $\mathcal L^{\Delta_5}$ on
$\overline{\mathcal A_2}$ has monodromy of order~$8$ around the
Humbert divisor $H_1$ (Bruinier 2002, Proposition~5.1,
Heegner Chern-class reciprocity), and this order-$8$
$\mathbb Z/8$ class in $\mathrm{CH}^1(H_1)$ is the
Hodge-theoretic boundary value that any transfer between the
elliptic chart $U_{13}$ and the Kontsevich chart $U_{14}$ must
respect. It is not, by itself, an element of the prounipotent
group $\mathrm{GRT}_1(\bQ)$. Producing an actual Tamarkin
transfer datum requires a logarithmic/prounipotent comparison map
from this Humbert monodromy class to the completed associator
torsor. Under such a lift, the identity
$\hbar^2\cdot K^{\kappa_{\mathrm{ch}}}=-1$ with
$\hbar^2=-1/8$ gives the numerical boundary condition for the
chart transition on the K3 component.
\end{remark}
