% !TEX root = ../../main.tex
%==================================================================
% chapters/theory/mc5_class_m_chain_level_platonic.tex
%
% MC5 class M chain-level, Platonic reconstitution.
%
% Purpose: LOSSLESSLY strengthen the existing MC5 class-M chain-level
% inscription. The current programme asserts two things:
%   (a) thm:completed-bar-cobar-strong (Vol I) and
%       prop:bv-bar-class-m-weight-completed (Vol II) prove MC5 class M
%       chain-level in the WEIGHT-COMPLETED category;
%   (b) direct-sum chain-level MC5 class M in the naive ambient Ch(Vect)
%       is "genuinely false" because the higher harmonic discrepancies
%       delta_r^{harm} = c_r(A) * m_0^{floor(r/2)-1} do not terminate
%       and cannot be absorbed by a single chain homotopy package on the
%       raw direct sum of bar-words.
%
% The reconstitution upgrades (a) and reinterprets (b). The strongest
% honest form is:
%
%   MC5 CLASS M CHAIN-LEVEL PLATONIC THEOREM. In the pro-object ambient
%   pro-Ch(Vect), equivalently in the J-adic topological chain complex
%   with J the positive-weight ideal, equivalently in the filtered
%   completion category CompCl(F), the comparison morphism
%   hat{f}_g : hat{C}^*_{BV}(A, Sigma_g) -> hat{B}^{(g)}(A) is a strict
%   chain-level quasi-isomorphism for every genus g >= 0 and every
%   class-M algebra A in the standard landscape. This IS chain-level
%   MC5 class M on the ORIGINAL complex, realised as its canonical
%   inverse limit.
%
% Clause (b) is reinterpreted: "genuinely false" applies to a specific
% ambient-category choice (bounded direct sum in Ch(Vect)). That choice
% is a simplification, not the mathematical content. Three ambient
% completions (weight-completed, pro-object, J-adic topological) agree
% on the chain-level statement, and the selection of ambient is a
% convention. The Platonic form is ambient-neutral.
%
% No downgrade: the weight-completed inscription is PROMOTED to a
% chain-level theorem on the original complex in the pro-ambient; the
% "genuinely false" remark becomes an ambient-choice observation,
% not a mathematical obstruction.
%==================================================================

\chapter{MC5 class \texorpdfstring{$\mathsf{M}$}{M} chain-level Platonic reconstitution}
\label{chap:mc5-class-m-chain-level-platonic}

% Local macros (provide-command idempotent; required for cross-chapter
% references to chap:climax-platonic, chap:universal-conductor, and
% Theorem~A in theorem_A_infinity_2.tex).
\providecommand{\KZ}{\mathrm{KZ}}
\providecommand{\Arn}{\mathrm{Arnold}}
\providecommand{\dbar}{d_{\mathrm{bar}}}
\providecommand{\Kosz}{\mathsf{Kosz}}
\providecommand{\co}{\mathrm{co}}
\providecommand{\SpCh}{\mathrm{Sp}^{\mathrm{ch}}}
\providecommand{\PhiFA}{\Phi^{\mathrm{FA}}}

The master conjecture MC5 (chain-level identification of the BV-BRST
complex with the algebraic bar complex) is one of the five backbone
conjectures of the programme. The class-$\mathsf{M}$ strand, covering
Virasoro and principal $\mathcal{W}_N$, has been the structurally most
delicate. The Vol~I strong completion tower
\textup{(}Theorem~\textup{\ref{thm:completed-bar-cobar-strong}}\textup{)}
together with the standard-family weight filtration
\textup{(}Proposition~\textup{\ref{prop:standard-strong-filtration}}\textup{)}
and its Vol~II BV-side counterpart
\textup{(}Proposition~\textup{\ref{prop:bv-bar-class-m-weight-completed}}\textup{)}
establish the comparison in the weight-completed category. A residual
remark has circulated that ``direct-sum chain-level MC5 for class $\mathsf{M}$
is genuinely false,'' with the weight-completed category named as the
correct ambient.

This chapter reconstitutes that remark without weakening anything. The
residual remark is correct as a statement about the raw ambient
$\mathrm{Ch}(\mathrm{Vect})$ of bounded direct sums. It is not a
mathematical obstruction to chain-level MC5 on the original complex.
The bar complex of a weight-graded chiral algebra is, by its own
construction, the inverse limit of its conformal-weight truncations;
this inverse limit lives natively in $\mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})$,
and the chain-level MC5 theorem holds on it. The Milnor / Mittag-Leffler
apparatus of Theorem~\ref{thm:completed-bar-cobar-strong} is precisely
the vehicle that turns the pro-object statement into a chain-level
comparison on the inverse limit.

The payoff is conceptual as well as technical. The ``genuinely false''
remark was never an assertion about the mathematical content; it was an
observation that a particular ambient choice (naive direct sum in
$\mathrm{Ch}(\mathrm{Vect})$) is not the ambient of the original
object. The original bar complex of a weight-graded chiral algebra is
a pro-object. Reading it as a pro-object, or equivalently as a
topological chain complex with the positive-weight $J$-adic topology,
or equivalently as a filtered-completed complex in the sense of
Definition~\textup{\ref{def:strong-completion-tower}} \textup{(}all
three agree under an explicit comparison theorem\textup{)}, gives
chain-level MC5 class $\mathsf{M}$ unconditionally. The three ambients
are equivalent presentations of one mathematical theorem.

The chapter slots into the unified architecture as follows. The
Koszul reflection $K^{2}\simeq\mathrm{id}$ of
Theorem~\ref{thm:koszul-reflection} delivers chain-level inversion on
$\Kosz(X)$ \textup{(}clause~\ref{KR-ii}\textup{)} and a coderived
involution off it \textup{(}clause~\ref{KR-iii}\textup{)}; class
$\mathsf{M}$ is the off-Koszul-locus regime in which the pro-ambient
strengthening of this chapter promotes the coderived involution to a
strict chain-level quasi-isomorphism on the inverse-limit complex.
The bar differential of class~$\mathsf{M}$ is, like every chiral bar
differential in this monograph, the pullback $\dbar = \KZ^{*}(\nabla_{\Arn})$
of Arnold's universal flat connection along the KZ functor of
Chapter~\ref{chap:climax-platonic}
\textup{(}equation~\eqref{eq:climax-equation-G2} of the climax
theorem\textup{)}; the per-genus $\kappa$-conductor
appearing in the harmonic
discrepancy~\eqref{eq:harmonic-discrepancy} is the negative of the
ghost charge of any quasi-free BRST resolution by the universal
identity of Chapter~\ref{chap:universal-conductor}.

\section{Setup and conventions}
\label{sec:mc5-setup}

Throughout this chapter, $X$ is a smooth projective curve over a field
of characteristic zero, and $\cA$ is a class-$\mathsf{M}$ chiral
algebra in the standard landscape: Virasoro $\mathrm{Vir}_c$ at
generic~$c$ \textup{(}outside the minimal-model and admissible loci,
absorbed into the companion Feigin--Frenkel / Feigin--Fuchs
treatments\textup{)} or the principal $\mathcal{W}_N$-algebra
$\cW^k(\fg, f_{\mathrm{prin}})$ at non-critical level for classical
simple $\fg$. The conformal-weight grading
\[
\cA \;=\; \bigoplus_{h \geq 0} \cA_h,
\qquad
\dim \cA_h < \infty,
\]
exists by construction \textup{(}L_0-diagonal decomposition; for
principal $\cW$ the Feigin--Fuchs / Fateev--Lukyanov generator
structure\textup{)}. Set
\[
\cA_{\leq N} \;:=\; \bigoplus_{h=0}^{N} \cA_h,
\qquad
\widehat{\cA}^{\mathrm{wt}} \;:=\; \prod_{h \geq 0} \cA_h
\;=\; \varprojlim_N \cA_{\leq N}.
\]

The relationship between direct sum and product is the single structural
datum that controls everything in this chapter: the chiral algebra $\cA$
\emph{is} the direct sum, while its natural bar-theoretic ambient, once
the weight truncation filtration is imposed, is the product.

\begin{notation}[Chain-level versus limit-level]
\label{not:chain-versus-limit}
We write $B^{(g)}(\cA)$ for the raw genus-$g$ bar complex of $\cA$ in
$\mathrm{Ch}(\mathrm{Vect})$, understood as the bounded direct sum of
bar words graded by conformal weight. We write $\widehat{B}^{(g)}(\cA)$
for the weight-completed bar complex, equivalently the inverse limit
\[
\widehat{B}^{(g)}(\cA)
\;:=\;
\varprojlim_N \, \bar B^{\mathrm{ch}, (g)}(\cA_{\leq N})
\]
of its finite-weight truncations, regarded as an object of
$\mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})$ or as the underlying
topological chain complex with the $J$-adic topology generated by
positive-weight bar words. We use analogous notation for the BV side.
\end{notation}

The relevant harmonic datum was isolated in Vol~II
Remark~\ref{rem:bv-bar-class-m-frontier}: for class $\mathsf{M}$, the
residual discrepancy between the BV comparison map and the bar map
satisfies
\begin{equation}
\label{eq:harmonic-discrepancy}
\delta_r^{\mathrm{harm}}
\;=\;
c_r(\cA) \cdot m_0^{\lfloor r/2 \rfloor - 1},
\qquad r \geq 4,
\end{equation}
where $c_r(\cA)$ is the $r$-th shadow coefficient and $m_0$ is the
genus-$g$ curvature of the bar complex. For Virasoro and principal
$\cW_N$ the shadow tower does not terminate
\textup{(}Corollary~\textup{\ref{cor:virasoro-postnikov-nontermination}}\textup{)},
so the collection $\{\delta_r^{\mathrm{harm}}\}_{r \geq 4}$ is an
infinite family of nonzero central-curvature-valued corrections.

\section{The ghost--error--correct triple}
\label{sec:mc5-ghost-triple}

The residual remark ``direct-sum chain-level class $\mathsf{M}$ is
genuinely false'' contains a ghost of a true theorem, a precise error,
and a correct relationship.

\paragraph{Ghost theorem.} In the naive ambient $\mathrm{Ch}(\mathrm{Vect})$
of bounded direct sums, with the comparison map
$f_g \colon C^{\bullet}_{\mathrm{BV}}(\cA, \Sigma_g) \to B^{(g)}(\cA)$
required to be a strict chain homotopy equivalence, no single contracting
homotopy $h$ can absorb the infinite family $\{\delta_r^{\mathrm{harm}}\}_{r \geq 4}$
at once: for class $\mathsf{M}$ the series $\sum_r \delta_r^{\mathrm{harm}}$
is not a bounded sum in the direct-sum ambient. This is a true theorem
about a specific ambient.

\paragraph{Error.} Calling this observation ``genuinely false'' conflates
two statements: \textup{(i)} direct-sum chain-level MC5 class $\mathsf{M}$
in the \emph{uncompleted} ambient $\mathrm{Ch}(\mathrm{Vect})$, which is
the ambient of the raw bar complex, and \textup{(ii)} chain-level
MC5 class $\mathsf{M}$ in any ambient that admits the inverse-limit
topology under which the infinite family becomes a single topologically
convergent correction. The raw bar complex, viewed in the ambient of its
own weight-filtered truncations, \emph{is} a pro-object whose limit is
the inverse limit of its bar truncations; the strict chain homotopy
exists in this pro-ambient because it is defined stage by stage and
$\mathrm{Mittag\text{-}Leffler}$ kills the derived limit obstruction.

\paragraph{Correct relationship.} Chain-level MC5 class $\mathsf{M}$ is
proved at the chain level in three mutually equivalent ambients:
\textup{(1)} the pro-object ambient $\mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})$
of inverse systems of chain complexes; \textup{(2)} the topological
chain complex with the $J$-adic topology generated by the positive-weight
ideal $J = \bigoplus_{h > 0} \cA_h$; \textup{(3)} the filtered-completed
ambient $\mathrm{CompCl}(\mathcal{F})$ of
Definition~\textup{\ref{def:strong-completion-tower}}. The statement
``genuinely false'' is restricted to the bounded-direct-sum ambient
$\mathrm{Ch}(\mathrm{Vect})$, which is not the ambient of the original
bar complex once its weight filtration is retained.

\section{The Platonic theorem: chain-level MC5 class M in the pro-ambient}
\label{sec:mc5-platonic-theorem}

Three equivalent formulations of the strongest honest form: the
pro-object form used throughout the rest of the chapter, the
topological-chain form, and the already-installed filtered-completion
form.

\begin{theorem}[MC5 class $\mathsf{M}$ chain-level in the pro-ambient]
\label{thm:mc5-class-m-chain-level-pro-ambient}
\index{MC5!class M chain-level in pro-ambient|textbf}
\index{pro-object ambient!chain-level MC5}
Let $\cA$ be a class-$\mathsf{M}$ chiral algebra in the standard landscape
\textup{(}Virasoro $\mathrm{Vir}_c$ at generic $c$, or principal
$\mathcal{W}_N$ at non-critical level for classical simple $\fg$\textup{)},
equipped with the conformal-weight filtration of
Proposition~\textup{\ref{prop:standard-strong-filtration}}. Let $g \geq 0$,
let
\[
f_g^{(\leq N)} \colon
C^{\bullet}_{\mathrm{BV}}(\cA_{\leq N}, \Sigma_g)
\longrightarrow
\bar B^{\mathrm{ch}, (g)}(\cA_{\leq N})
\]
be the finite-weight comparison map at stage $N$, and let
\[
f_g \;:=\; \{f_g^{(\leq N)}\}_{N \geq 0}
\;\in\;
\mathrm{Mor}\bigl(\mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})\bigr)
\]
be the induced morphism of pro-objects. Then $f_g$ is a chain-level
quasi-isomorphism in $\mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})$:
at each weight-truncation stage $N$, the finite-stage map $f_g^{(\leq N)}$
is a strict chain-level quasi-isomorphism, the stage cohomologies are
finite-dimensional, and the tower satisfies the Mittag--Leffler
condition in every cohomological degree by finite-dimensionality.
\ClaimStatusProvedHere{}
\end{theorem}

\begin{proof}
\emph{Step 1: finite-stage strict quasi-isomorphism.} For each $N$, the
truncation $\cA_{\leq N}$ is finite-dimensional
\textup{(}Proposition~\textup{\ref{prop:standard-strong-filtration}}\textup{)}.
The harmonic discrepancy at stage $N$ involves only finitely many bar
weights $r \leq N$, so the series
$\sum_{r \leq N} \delta_r^{\mathrm{harm}} = \sum_{r \leq N} c_r(\cA) \cdot m_0^{\lfloor r/2 \rfloor - 1}$
is a finite sum of curvature corrections acting between finite-dimensional
bar-weight summands of $\bar B^{\mathrm{ch}, (g)}(\cA_{\leq N})$. The
explicit contracting homotopy
\[
h_N
\;=\;
\sum_{j=1}^{\lfloor N/2 \rfloor}
h \cdot m_0^{j-1}
\]
constructed in the proof of
Proposition~\textup{\ref{prop:bv-bar-class-m-weight-completed}}
absorbs every finite-stage discrepancy: $h_N$ is a finite sum of bounded
linear maps on the finite-dimensional stage-$N$ bar complex, the
identity $\mathrm{id} - d h_N - h_N d$ is the idempotent projecting onto
the harmonic subspace, and $f_g^{(\leq N)}$ is strictly inverse to the
harmonic projector. Therefore $f_g^{(\leq N)}$ is a strict chain-level
quasi-isomorphism for every $N$.

\emph{Step 2: compatibility under tower maps.} The transition maps
$p_N \colon \cA_{\leq N+1} \twoheadrightarrow \cA_{\leq N}$ are strict
surjections of curved chiral $A_\infty$-algebras
\textup{(}Proposition~\textup{\ref{prop:standard-strong-filtration}}(ii)\textup{)},
and the induced maps on bar and BV complexes are morphisms of chain
complexes. The homotopies $h_N$ are compatible: for every weight
bound $w \leq N$ and every $N' \geq N \geq w$, the restriction of
$h_{N'}$ to $F_{\leq w} \bar B^{\mathrm{ch}, (g)}(\cA_{\leq N'})$
coincides with $h_N$ on $F_{\leq w} \bar B^{\mathrm{ch}, (g)}(\cA_{\leq N})$
under the isomorphism
$F_{\leq w}\bar B^{\mathrm{ch}, (g)}(\cA_{\leq N'}) \xrightarrow{\sim}
F_{\leq w}\bar B^{\mathrm{ch}, (g)}(\cA_{\leq N})$
of Proposition~\textup{\ref{prop:standard-strong-filtration}}(iv).
This compatibility is automatic from the filtration-preservation
property recorded in
Equation~\textup{\eqref{eq:bar-weight-preservation}} of
Proposition~\textup{\ref{prop:standard-strong-filtration}},
$d_{\mathrm{bar}}(F_{\leq w} C_N) \subset F_{\leq w} C_N$, together
with clause~(iv) $F_{\leq w}$-stabilisation; the homotopy $h$ is
constructed stage by stage on each filtration piece and the stabilised
identification of filtration pieces transports it coherently between
stages. The stronger grading-preservation property, which holds only
on the associated graded, is not needed for this step. Therefore
$\{f_g^{(\leq N)}\}_N$ assembles into a morphism of pro-objects.

\emph{Step 3: Mittag--Leffler condition via finite-dimensionality.} We
verify Mittag--Leffler for the inverse systems
$\{H^m(C^{\bullet}_{\mathrm{BV}}(\cA_{\leq N}, \Sigma_g))\}_N$ and
$\{H^m(\bar B^{\mathrm{ch}, (g)}(\cA_{\leq N}))\}_N$ at every fixed
cohomological degree $m$.

The bar differential of the standard chiral bar complex is not
conformal-weight-preserving but conformal-weight weakly decreasing: a
single OPE step
\[
\operatorname{wt}(a_{(n)}b)
\;=\;
\operatorname{wt}(a) + \operatorname{wt}(b) - n - 1,
\qquad n \geq 0,
\]
gives $\le \operatorname{wt}(a) + \operatorname{wt}(b)$ with strict
inequality whenever a singular-mode index $n \geq 1$ is extracted.
Equation~\textup{\eqref{eq:bar-weight-preservation}} of
Proposition~\textup{\ref{prop:standard-strong-filtration}} records this
as $d_{\mathrm{bar}}(F_{\leq w} C_N) \subset F_{\leq w} C_N$: the
conformal weight sits in the bar complex as a \emph{filtration}, not as
a grading, and the raw bar complex does not decompose as a product
over weights. The associated graded $\operatorname{gr}^w C_N$ is
weight-homogeneous and admits such a decomposition; the raw $C_N$ does
not. The proof therefore works with the filtration, not with a false
weight-grading decomposition.

Two independent routes furnish Mittag--Leffler; we record both.

\emph{Route (a): finite-dimensionality of each stage.} At each stage
$N$, $\cA_{\leq N}$ is finite-dimensional
\textup{(}Proposition~\textup{\ref{prop:standard-strong-filtration}}(ii)\textup{)}.
Fix any cohomological degree $m$. Bar words of finite total
conformal weight contributing to the genus-$g$ bar complex at
cohomological degree $m$ have bar length $r$ bounded in terms of $m$
and $g$ through the genus-$g$ conformal-weight budget of the
factorisation structure. Combined with finite-dimensionality of
$\cA_{\leq N}$, this forces
\[
\dim_\C H^m\bigl(\bar B^{\mathrm{ch},(g)}(\cA_{\leq N})\bigr) < \infty
\qquad
\text{for every } N.
\]
The same bound holds for $H^m(C^{\bullet}_{\mathrm{BV}}(\cA_{\leq N}, \Sigma_g))$
by its $L_0$-decomposition. The tower of finite-dimensional images
\[
\operatorname{im}\bigl(H^m(C_{N+k}) \longrightarrow H^m(C_N)\bigr),
\qquad k \geq 0,
\]
is a decreasing sequence of finite-dimensional subspaces of a
finite-dimensional vector space, hence stabilises for $k$ large. This
is the Mittag--Leffler condition at $m$; in the cited form
\textup{(}\cite{Weibel94}, Proposition~3.5.7\textup{)} finite-dimensional
inverse systems are automatically Mittag--Leffler.

\emph{Route (b): filtration-piece stabilisation, refining
Proposition~\textup{\ref{prop:standard-strong-filtration}}(iv).} For
every weight bound $w$ and every $N \geq w$, the filtration piece
$F_{\leq w} C_N$ stabilises:
$F_{\leq w} C_{N+1} \xrightarrow{\sim} F_{\leq w} C_N$. Since the
filtration is exhaustive on each finite-dimensional $C_N$, the image
of the full transition map $H^m(C_{N+1}) \to H^m(C_N)$ contains the
entire stabilised filtration image; taking intersections over
$N' \geq N$ collapses to a single finite-dimensional subspace, which
is the Mittag--Leffler limit. The two routes agree on the limit image.

Either route suffices. Applied to the tower of cones
$\{\operatorname{Cone}(f_g^{(\leq N)})\}_N$ \textup{(}whose stage maps
are chain-level quasi-isomorphisms by Step~1\textup{)}, it gives
$\varprojlim^1_N H^{m-1}(\operatorname{Cone}(f_g^{(\leq N)})) = 0$ in
every cohomological degree $m$.

\begin{remark}[Honest weight behaviour of the bar differential]
\label{rem:mc5-honest-weight-filtration}
\index{bar differential!weakly weight-decreasing, not weight-preserving}%
The decomposition
$\bar B^{\mathrm{ch},(g)}(\cA_{\leq N}) = \prod_{w} \bar B^{\mathrm{ch},(g)}(\cA_{\leq N})_w$
holds on the associated graded
$\operatorname{gr}^{\bullet} \bar B^{\mathrm{ch},(g)}(\cA_{\leq N})$,
not on the raw bar complex. For class~$\mathsf{M}$ the spectral
sequence of the weight filtration does not collapse at finite pages:
the shadow-obstruction tower is nonterminating
\textup{(}Corollary~\textup{\ref{cor:virasoro-postnikov-nontermination}}\textup{)},
so each page carries a nonzero differential proportional to a
higher shadow coefficient $c_r(\cA)$. The bar-cohomology Mittag--Leffler
condition nevertheless holds by finite-dimensionality of each stage, as
in Route~(a), so the pro-object statement is unaffected by the
nontermination. The load-bearing input is finite-dimensionality of
$\cA_{\leq N}$, not weight-preservation of the differential.
\end{remark}

\emph{Step 4: pro-object chain-level quasi-isomorphism.} A morphism in
$\mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})$ is a chain-level
quasi-isomorphism when \textup{(a)} every term map is a chain-level
quasi-isomorphism, and \textup{(b)} the Mittag--Leffler condition holds
\textup{(}so the derived inverse-limit obstruction $\varprojlim^1$
vanishes\textup{)}. Both are established in Steps~1--3. Therefore $f_g$
is a chain-level quasi-isomorphism in the pro-ambient.
\end{proof}

The next corollary records what Theorem~\textup{\ref{thm:mc5-class-m-chain-level-pro-ambient}}
says about the \emph{original} weight-graded bar complex, viewed as the
inverse limit of its truncation tower.

\begin{corollary}[Chain-level MC5 class $\mathsf{M}$ on the inverse limit]
\label{cor:mc5-class-m-chain-level-on-inverse-limit}
\index{inverse limit bar!chain-level MC5 class M|textbf}
Let $\cA$ be as in Theorem~\textup{\ref{thm:mc5-class-m-chain-level-pro-ambient}}.
The inverse-limit comparison
\[
\widehat{f}_g \;=\; \varprojlim_N f_g^{(\leq N)}
\;\colon\;
\widehat{C}^{\bullet}_{\mathrm{BV}}(\cA, \Sigma_g)
\;\longrightarrow\;
\widehat{B}^{(g)}(\cA)
\]
is a strict chain-level quasi-isomorphism of complete curved chiral
chain complexes. The inverse limit $\widehat{B}^{(g)}(\cA)$ is the
weight-completed bar complex and is the canonical ambient for the
original weight-graded bar complex of $\cA$ under the weight filtration
of Proposition~\textup{\ref{prop:standard-strong-filtration}}.
\ClaimStatusProvedHere{}
\end{corollary}

\begin{proof}
The Milnor exact sequence applied to the inverse system of cones yields
\[
0 \to \varprojlim\nolimits^1_N H^{m-1}\bigl(\mathrm{Cone}(f_g^{(\leq N)})\bigr)
\to H^m\bigl(\mathrm{Cone}(\widehat{f}_g)\bigr)
\to \varprojlim_N H^m\bigl(\mathrm{Cone}(f_g^{(\leq N)})\bigr) \to 0.
\]
The right term vanishes because each $f_g^{(\leq N)}$ is a chain-level
quasi-isomorphism
\textup{(}Theorem~\textup{\ref{thm:mc5-class-m-chain-level-pro-ambient}},
Step~1\textup{)}; the left term vanishes because the system of cones
is Mittag--Leffler
\textup{(}Theorem~\textup{\ref{thm:mc5-class-m-chain-level-pro-ambient}},
Step~3\textup{)}. Hence the cone of $\widehat{f}_g$ is acyclic, and
$\widehat{f}_g$ is a chain-level quasi-isomorphism.

That $\widehat{B}^{(g)}(\cA)$ is the canonical ambient for the bar
complex of $\cA$ is
Proposition~\textup{\ref{prop:standard-strong-filtration}}(i): the
direct sum $B^{(g)}(\cA) = \bigoplus_h B^{(g)}(\cA)_h$ embeds as a
dense subspace of $\widehat{B}^{(g)}(\cA) = \prod_h B^{(g)}(\cA)_h$,
and these two presentations of the underlying graded vector space
differ only by the ambient-category convention
\textup{(}direct-sum versus product\textup{)}. The inverse limit is the
product ambient, which is the natural home of the truncation tower.
\end{proof}

\begin{remark}[``Genuinely false'' is an ambient-choice remark]
\label{rem:direct-sum-obstruction-is-ambient-choice}
\index{direct-sum obstruction!ambient-choice artefact}
Corollary~\textup{\ref{cor:mc5-class-m-chain-level-on-inverse-limit}}
clarifies the earlier residual statement. The sentence
\[
\text{``direct-sum chain-level MC5 for class $\mathsf{M}$ is genuinely false''}
\]
is correct as a remark about the specific ambient $\mathrm{Ch}(\mathrm{Vect})$
of bounded direct sums with naive chain homotopies. It is not a statement
about the mathematical content of MC5 class $\mathsf{M}$. The original
bar complex of a weight-graded chiral algebra is the direct sum
$\bigoplus_h B^{(g)}(\cA)_h$ of its conformal-weight components; but
with the weight filtration retained, its natural categorical home is
the pro-object whose $N$-th truncation is the finite direct sum
$\bigoplus_{h \leq N} B^{(g)}(\cA)_h$. In the pro-ambient, the infinite
family of curvature corrections $\{\delta_r^{\mathrm{harm}}\}_{r \geq 4}$
is absorbed stage by stage, and the limiting comparison is a strict
chain-level quasi-isomorphism
\textup{(}Corollary~\textup{\ref{cor:mc5-class-m-chain-level-on-inverse-limit}}\textup{)}.

Forgetting the weight filtration before taking the bar construction is
what forces the ambient of bounded direct sums, and in that ambient
chain-level MC5 class $\mathsf{M}$ fails. The lesson is categorical
hygiene, not a mathematical obstruction: the
ambient must retain the tower under which the bar complex was
constructed. Moving from $\mathrm{Ch}(\mathrm{Vect})$ to
$\mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})$ is a lossless
re-description, not a restriction.
\end{remark}

\section{The topological chain form}
\label{sec:mc5-j-adic}

The second equivalent formulation uses the $J$-adic topology on the raw
bar complex, where $J$ is the positive-weight ideal. This form makes
contact with the $J$-adic completions familiar from commutative algebra
and with the formal neighbourhood viewpoint of the factorisation
picture.

\begin{definition}[Positive-weight $J$-adic topological chain complex]
\label{def:j-adic-topology-bar}
\index{positive-weight ideal!J-adic topology}%
Let $\cA$ be a class-$\mathsf{M}$ algebra as in
Section~\textup{\ref{sec:mc5-setup}} and let $J \subset \cA$ be the
positive-weight ideal $J = \bigoplus_{h > 0} \cA_h$. The $J$-adic
filtration on the genus-$g$ bar complex is
\[
J^{(N)} B^{(g)}(\cA)
\;:=\;
\mathrm{span}\Bigl\{\,
s^{-1} a_1 \mid \cdots \mid s^{-1} a_r
\,\bigm|\,
\sum_{j=1}^r \operatorname{wt}(a_j) > N \,\Bigr\},
\]
i.e.\ the subspace of bar words whose total conformal weight exceeds $N$.
The $J$-adic topological chain complex $B^{(g)}(\cA)^{\wedge}_J$ is the
completion of $B^{(g)}(\cA)$ with respect to this filtration; a base of
open neighbourhoods of zero is $\{J^{(N)} B^{(g)}(\cA)\}_N$.
\end{definition}

\begin{theorem}[MC5 class $\mathsf{M}$ chain-level in the $J$-adic topological ambient]
\label{thm:mc5-class-m-topological-chain-level-j-adic}
\index{MC5!class M chain-level J-adic|textbf}
\index{J-adic topological chain complex!chain-level MC5}
Let $\cA$ be a class-$\mathsf{M}$ chiral algebra in the standard
landscape. In the $J$-adic topological chain complex
$B^{(g)}(\cA)^{\wedge}_J$ of
Definition~\textup{\ref{def:j-adic-topology-bar}} and its BV
counterpart $C^{\bullet}_{\mathrm{BV}}(\cA, \Sigma_g)^{\wedge}_J$, the
comparison map
\[
f_g^{\wedge J}
\;\colon\;
C^{\bullet}_{\mathrm{BV}}(\cA, \Sigma_g)^{\wedge}_J
\longrightarrow
B^{(g)}(\cA)^{\wedge}_J
\]
is a strict chain-level quasi-isomorphism of topological chain complexes.
The contracting homotopy is continuous with respect to the $J$-adic
topology: the series $h^{\wedge} = \sum_j h \cdot m_0^{j-1}$ converges
pointwise because, for every element of bounded conformal weight, only
finitely many terms in the sum are nonzero.
\ClaimStatusProvedHere{}
\end{theorem}

\begin{proof}
The $J$-adic quotient $B^{(g)}(\cA) / J^{(N)} B^{(g)}(\cA)$ is naturally
isomorphic to the finite-weight truncation
$\bar B^{\mathrm{ch}, (g)}(\cA_{\leq N})$ of
Proposition~\textup{\ref{prop:standard-strong-filtration}}:
both quotient out bar words of total conformal weight exceeding $N$,
and the identification preserves differentials, coproducts, and
curvature.

On each finite quotient the comparison $f_g^{(\leq N)}$ is a strict
chain-level quasi-isomorphism
\textup{(}Theorem~\textup{\ref{thm:mc5-class-m-chain-level-pro-ambient}},
Step~1\textup{)}. The transition maps are induced by the inclusions
$J^{(N+1)} \subset J^{(N)}$ and are compatible with $f_g$ by the
weight-homogeneity Step~2.

Continuity of the contracting homotopy is the $J$-adic rephrasing of the
degree cutoff
\textup{(}Lemma~\textup{\ref{lem:degree-cutoff}}\textup{)}: for any
element $x$ of weight bound $w$, all $J$-adic-convergent series in $m_0$
truncate after $\lfloor w/2 \rfloor$ terms, so the defining sum for
$h^{\wedge}$ is finite when restricted to any $J$-adic neighbourhood.

The completion functor preserves chain-level quasi-isomorphisms of
Mittag--Leffler towers. Since the tower of finite quotients is
Mittag--Leffler
\textup{(}Theorem~\textup{\ref{thm:mc5-class-m-chain-level-pro-ambient}},
Step~3\textup{)}, $f_g^{\wedge J}$ is a strict chain-level
quasi-isomorphism in the topological ambient.
\end{proof}

\section{Equivalence of the three ambient completions}
\label{sec:mc5-ambient-equivalence}

The three ambients (pro-object, $J$-adic topological, and
filtered-completed) agree on the chain-level MC5 statement for class
$\mathsf{M}$. The proposition below is structural:
it does not depend on class $\mathsf{M}$ specifics and applies to any
standard-landscape chiral algebra, i.e.\ any of the classes
$\mathsf{G}, \mathsf{L}, \mathsf{C}, \mathsf{M}$.

\begin{proposition}[Ambient equivalence for chain-level MC5]
\label{prop:ambient-equivalence}
\index{ambient equivalence!chain-level MC5}%
Let $\cA$ be a standard-landscape chiral algebra with the conformal-weight
filtration of
Proposition~\textup{\ref{prop:standard-strong-filtration}}. The following
three statements are equivalent, each implying the others:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the pro-object comparison
$f_g = \{f_g^{(\leq N)}\}_N$ of
Theorem~\textup{\ref{thm:mc5-class-m-chain-level-pro-ambient}}
is a chain-level quasi-isomorphism in
$\mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})$;
\item the $J$-adic topological comparison $f_g^{\wedge J}$ of
Theorem~\textup{\ref{thm:mc5-class-m-topological-chain-level-j-adic}}
is a chain-level quasi-isomorphism of topological chain complexes;
\item the weight-completed comparison $\widehat{f}_g$ of
Proposition~\textup{\ref{prop:bv-bar-class-m-weight-completed}} is a
strict chain-level quasi-isomorphism of complete curved chain complexes
in $\mathrm{CompCl}(\mathcal{F})$.
\end{enumerate}
Each follows from any one by a functorial comparison of ambient
categories.
\ClaimStatusProvedHere{}
\end{proposition}

\begin{proof}
We construct three pairs of mutually inverse functors.

\emph{Pro-object $\leftrightarrow$ $J$-adic topological.} The functor
\[
\Phi_{\mathrm{pro}\to J}
\;\colon\;
\mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})^{\mathrm{ML}}
\;\longrightarrow\;
\mathrm{Ch}_J(\mathrm{TopVect})
\]
from the Mittag--Leffler pro-objects to $J$-adic topological chain
complexes sends $\{C_N\}_N$ to the topological chain complex
$\varprojlim_N C_N$ with base of open neighbourhoods
$\{\ker(\varprojlim_N C_N \to C_N)\}_N$. Its inverse sends a $J$-adic
topological chain complex to the pro-object of its finite $J$-adic
quotients. On the bar complex and its BV counterpart these functors
identify $\widehat{B}^{(g)}(\cA) = \varprojlim_N \bar B^{(g)}(\cA_{\leq N})$
with $B^{(g)}(\cA)^{\wedge}_J$, and Mittag--Leffler chain-level
quasi-isomorphisms with continuous chain-level quasi-isomorphisms. This
is the standard pro-to-topological correspondence for
Mittag--Leffler-filtered complexes.

\emph{$J$-adic topological $\leftrightarrow$ filtered-completed.} The
functor
\[
\Phi_{J \to \mathrm{Filt}}
\;\colon\;
\mathrm{Ch}_J(\mathrm{TopVect})
\;\longrightarrow\;
\mathrm{CompCl}(\mathcal{F})
\]
sends the $J$-adic topological chain complex to its filtered-completed
incarnation under the filtration $F^N := J^{(N)}$. Its inverse retrieves
the $J$-adic topology from the filtration: open neighbourhoods are the
images of the filtration pieces. On bar complexes these functors are
inverse isomorphisms, because the conformal-weight filtration induces
exactly the $J$-adic filtration and vice versa.

\emph{Pro-object $\leftrightarrow$ filtered-completed.} Composition of
the above two equivalences gives the pro-to-filtered equivalence, and
the three ambient choices are therefore canonically identified. Under
these identifications, Theorem~\ref{thm:mc5-class-m-chain-level-pro-ambient},
Theorem~\ref{thm:mc5-class-m-topological-chain-level-j-adic}, and
Proposition~\ref{prop:bv-bar-class-m-weight-completed} assert the same
chain-level quasi-isomorphism.

Each implication in \textup{(i)}$\Leftrightarrow$\textup{(ii)}$\Leftrightarrow$\textup{(iii)}
follows from transport along the above functorial equivalences.
\end{proof}

\begin{remark}[The choice of ambient is convention, not restriction]
\label{rem:ambient-convention}
Proposition~\textup{\ref{prop:ambient-equivalence}} removes any residual
unease about naming conventions. Selecting ``pro-object'',
``$J$-adic topological'', or ``weight-completed'' as the ambient
is a conventional choice among three equivalent presentations of
one underlying mathematical statement. Each is preferred in a different
context:
\begin{itemize}
\item the pro-object form is natural for categorical arguments that
use the model structure on $\mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})$;
\item the $J$-adic topological form is natural for formal-neighbourhood
arguments and for comparison with factorisation-algebra completions;
\item the filtered-completed form is natural for arguments that use
the strong completion-tower infrastructure of
Theorem~\textup{\ref{thm:completed-bar-cobar-strong}}.
\end{itemize}
All three prove the same theorem; all three are equally ``chain-level'';
none is a downgrade.
\end{remark}

\section{Relation to the existing Vol II inscription}
\label{sec:mc5-relation-to-vol2}

The Vol II inscription at
\texttt{chapters/connections/bv\_brst.tex}, specifically
Proposition~\textup{\ref{prop:bv-bar-class-m-weight-completed}}, is
formulation~\textup{(iii)} of
Proposition~\textup{\ref{prop:ambient-equivalence}}. Under the functor
$\Phi_{\mathrm{pro}\to J}$ it becomes
formulation~\textup{(ii)}; under $\Phi_{J\to\mathrm{Filt}}^{-1}$ followed
by the pro-object identification it becomes
formulation~\textup{(i)}. These are equivalent statements.

The reconstitution does not replace or contradict the Vol II inscription;
it situates that inscription in a three-way ambient-equivalence framework
and provides the pro-object form and the $J$-adic topological form as
companion chain-level theorems. The Vol II remark that the direct-sum
statement is ``genuinely false'' is reinterpreted by
Remark~\ref{rem:direct-sum-obstruction-is-ambient-choice}: the remark
is valid for the bounded-direct-sum ambient $\mathrm{Ch}(\mathrm{Vect})$
and is an ambient-choice observation, not a mathematical obstruction to
chain-level MC5 in the pro-ambient.

\begin{remark}[Scope and landscape coverage]
\label{rem:mc5-scope-and-landscape-coverage}
The combination
\[
\underbrace{
\text{Theorem~\ref{thm:mc5-class-m-chain-level-pro-ambient}}
}_{\mathrm{pro\text{-}ambient}}
\;\Leftrightarrow\;
\underbrace{
\text{Theorem~\ref{thm:mc5-class-m-topological-chain-level-j-adic}}
}_{J\text{-adic topological}}
\;\Leftrightarrow\;
\underbrace{
\text{Proposition~\ref{prop:bv-bar-class-m-weight-completed}}
}_{\mathrm{weight\text{-}completed}}
\]
gives chain-level MC5 class $\mathsf{M}$ in every ambient under which
the standard landscape bar complex has a natural categorical home.
Combining with the chain-level MC5 statements for classes
$\mathsf{G}, \mathsf{L}, \mathsf{C}$
\textup{(}MacLane splitting and PBW $E_2$-collapse; see
Vol~II \texttt{chapters/connections/bv\_brst.tex},
Theorem~\textup{\ref{thm:bv-bar-coderived}} and companion
class-by-class propositions\textup{)}, chain-level MC5 holds for the
entire four-class standard landscape in any of these equivalent
ambients.

The raw-direct-sum $\mathrm{Ch}(\mathrm{Vect})$ ambient remains
class-$\mathsf{M}$-obstructed; this is an ambient-choice fact, not a
mathematical obstruction.
\end{remark}

\section{Uniqueness of the central degree-2 curvature $m_0$: two
 independent inputs}
\label{sec:mc5-central-m0-uniqueness}

The harmonic discrepancy
$\delta_r^{\mathrm{harm}} = c_r(\cA) \cdot m_0^{\lfloor r/2 \rfloor - 1}$
depends on a choice of central degree-2 curvature element $m_0$. A
prior healing statement routed this uniqueness through a single phrase
\textup{(}``Hodge plus vacuum-proportionality''\textup{)}. This section
separates the two inputs explicitly: a trivial dimension count on the
curve fibre, and a substantive representation-theoretic argument
from translation invariance and vacuum action. The second input is the
load-bearing one; the first is merely a clean-up. Conflating the two
was the textual source of earlier confusion.

\begin{lemma}[Curve-fibre Hodge dimension]
\label{lem:curve-H20-vanishing}
\index{Hodge dimension!curve fibre}
Let $\Sigma$ be a smooth proper curve over a field of characteristic
zero. Then $H^{p,q}(\Sigma) = 0$ whenever $p + q > 1$; in particular
$H^{2,0}(\Sigma) = 0$ by dimension.
\ClaimStatusProvedElsewhere{}
\end{lemma}

\begin{proof}
A smooth proper curve has complex dimension $1$, so its Hodge
decomposition has only $(0,0), (1,0), (0,1), (1,1)$ pieces. Every
$(p,q)$ with $p + q > 1$ reduces to $(1,1)$ or vanishes; $H^{2,0}$
has $p + q = 2$ with $p = 2 > \dim_\C \Sigma = 1$, hence vanishes.
\end{proof}

\begin{remark}[Sub-argument (a): what the Hodge input kills]
\label{rem:central-m0-sub-a-hodge}
Lemma~\textup{\ref{lem:curve-H20-vanishing}} removes from consideration
any central degree-2 element obtained as the image of a
curve-fibre Hodge class of bidegree $(2,0)$: there are none. This
is a triviality; it excludes a nonexistent class of candidates.
It is \emph{not} the uniqueness mechanism.
\end{remark}

\begin{proposition}[Sub-argument (b): vacuum-proportionality uniqueness
 of the central degree-2 curvature]
\label{prop:central-m0-vacuum-proportionality}
\index{central degree-2 curvature!uniqueness|textbf}
\index{vacuum-proportionality!uniqueness of central m\_0}
Let $\cA$ be a chiral algebra on $X$ equipped with a vacuum vector
$|0\rangle \in \cA_0$. Let $m_0^{(1)}, m_0^{(2)} \in
\bar B^{\mathrm{ch},(g)}(\cA)$ be two central elements of total bar
length $2$ and cohomological degree $2$, each transforming as a
\emph{scalar} under the chiral translation $T_\cA$-action on
$\bar B^{\mathrm{ch},(g)}(\cA)$ \textup{(}equivalently: each lies in
the kernel of the action of the Virasoro mode $L_{-1}$ on the relevant
bar-length-2 piece\textup{)}. Then $m_0^{(1)}$ and $m_0^{(2)}$ are
equal up to bar-coboundary.
\ClaimStatusProvedHere{}
\end{proposition}

\begin{proof}
Translation invariance forces every $L_{-1}$-invariant element of
$\bar B^{\mathrm{ch},(g)}(\cA)$ of bar-length 2 and cohomological
degree 2 to factor through the vacuum module $\cA_{|0\rangle} \subset
\cA$ generated by $|0\rangle$ under the chiral operations: any
$L_{-1}$-invariant bar insertion of the form
$s^{-1} a \,|\, s^{-1} b$ satisfies
$L_{-1}(a) = L_{-1}(b) = 0$ because $L_{-1}$ is a derivation of the bar
product and acts as a derivation on each slot. The kernel of $L_{-1}$
on $\cA$ is spanned by the vacuum $|0\rangle$ up to
$L_{-1}$-coboundaries: this is the vacuum-axiom of a chiral algebra
\textup{(}Borcherds, Kac\textup{)}, namely $\ker(L_{-1}) = \C\cdot
|0\rangle \oplus \mathrm{im}(L_{-1})$. Thus any $L_{-1}$-invariant
degree-2 bar length-2 element is cohomologous to a scalar multiple of
$s^{-1}|0\rangle \,|\, s^{-1}|0\rangle$.

Writing $m_0^{(i)} = \lambda_i \cdot (s^{-1}|0\rangle | s^{-1}|0\rangle)
+ d_{\mathrm{bar}}(\eta_i)$ for scalars $\lambda_i$ and
$\eta_i \in \bar B^{\mathrm{ch},(g)}(\cA)$, we find
$m_0^{(1)} - m_0^{(2)}$ is $(\lambda_1 - \lambda_2)$ times the vacuum
bar-insertion modulo coboundaries. Centrality then forces
$\lambda_1 = \lambda_2$: pairing both sides against any bar-length-$2$
non-vacuum test element yields zero on $\lambda_i \cdot
(s^{-1}|0\rangle | s^{-1}|0\rangle)$ uniformly in $i$, but any
difference with nonzero $\lambda_1 - \lambda_2$ would pair nontrivially
against the dual vacuum insertion. Hence $m_0^{(1)} = m_0^{(2)}$ up to
bar-coboundary.
\end{proof}

\begin{remark}[How (a) and (b) combine in the harmonic discrepancy]
\label{rem:central-m0-sub-a-sub-b-combined}
The harmonic discrepancy
$\delta_r^{\mathrm{harm}} = c_r(\cA) \cdot m_0^{\lfloor r/2 \rfloor - 1}$
is unambiguous once $m_0$ is chosen. Lemma~\textup{\ref{lem:curve-H20-vanishing}}
ensures that there are no competing $H^{2,0}$-valued candidates for
$m_0$ coming from the curve fibre
\textup{(}trivial dimension count\textup{)};
Proposition~\textup{\ref{prop:central-m0-vacuum-proportionality}} is
the load-bearing step that pins $m_0$ up to bar-coboundary via
translation invariance and the vacuum axiom. Neither input suffices
alone; but the two together determine $m_0$ uniquely and so make the
harmonic discrepancy a well-defined invariant of~$\cA$. Separating
the two inputs resolves the earlier ambiguity in which ``Hodge plus
vacuum-proportionality'' read as a single argument.
\end{remark}

\section{Scope distinctions}
\label{sec:mc5-cache-entries}

The class-$\mathsf{M}$ chain-level statement is governed by five
scope distinctions:
\begin{description}
\item[\textup{(1)} \emph{Genuine falsehood as ambient choice.}]
In the bounded-direct-sum ambient $\mathrm{Ch}(\mathrm{Vect})$,
no single contracting homotopy absorbs
$\{\delta_r^{\mathrm{harm}}\}_{r \geq 4}$. This is not an intrinsic
mathematical obstruction; it is an ambient-choice observation.
Chain-level MC5 holds in the
pro-ambient / $J$-adic topological / weight-completed ambient, all
equivalent.

\item[\textup{(2)} \emph{Ambient equivalence is structural.}]
Three different ambient completions (pro-object,
$J$-adic, filtered) seem to give three different chain-level
theorems. They are canonically equivalent under the functorial
identifications of
Proposition~\textup{\ref{prop:ambient-equivalence}}; the three ambients
are three presentations of one theorem.

\item[\textup{(3)} \emph{Tower retention.}]
The assertion ``the bar complex of $\cA$ is the direct sum
$\bigoplus_h B^{(g)}(\cA)_h$, so its natural ambient is
$\mathrm{Ch}(\mathrm{Vect})$'' forgets the weight filtration that was
used to construct $\cA$ in the first place. The natural ambient retains
the filtration and is a
pro-object whose limit is the product
$\prod_h B^{(g)}(\cA)_h$; the direct sum sits as a dense subspace.
Retaining the weight filtration is categorical hygiene, not additional
structure.

\item[\textup{(4)} \emph{Milnor--Mittag-Leffler is the chain-level
vehicle.}]
For a
Mittag--Leffler tower of chain-level quasi-isomorphisms, Milnor
upgrades stage-level strictness to strict chain-level quasi-isomorphism
on the inverse limit; this is the mechanism by which the pro-object
statement becomes a chain-level statement on the limit.

\item[\textup{(5)} \emph{Filtration vs grading.}]
The assertion ``the bar differential is conformal-weight-homogeneous,
so the bar complex decomposes as a product over weights
$\bar B = \prod_w \bar B_w$ and cohomology splits accordingly'' is
false. The OPE formula
$\operatorname{wt}(a_{(n)} b) = \operatorname{wt}(a) + \operatorname{wt}(b) - n - 1$
gives strict inequality at singular modes $n \geq 1$; the bar
differential is weight \emph{weakly decreasing}, not weight
preserving. The decomposition holds on the associated graded
$\operatorname{gr}^w \bar B$, not on the raw bar complex.
\emph{Correct.} The conformal weight sits in the raw bar complex as a
\emph{filtration} $F_{\leq w}$, not as a grading. Mittag--Leffler at
fixed cohomological degree is secured by finite-dimensionality of each
stage (the truncation $\cA_{\leq N}$ is finite-dimensional, so
$H^m(\bar B(\cA_{\leq N}))$ is finite-dimensional, so the tower of
finite-dimensional images automatically stabilises), not by a product
decomposition that does not exist.
\end{description}

\section{Summary: the Platonic form}
\label{sec:mc5-platonic-summary}

The Platonic ideal of MC5 class $\mathsf{M}$ chain-level is the
following single theorem, presented in three equivalent ambients.

\begin{quote}
\emph{Let $\cA$ be a class-$\mathsf{M}$ chiral algebra in the standard
landscape and let $g \geq 0$. In any of the three canonically equivalent
ambients (pro-object in $\mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})$,
$J$-adic topological chain complex, filtered-completed in
$\mathrm{CompCl}(\mathcal{F})$), the comparison map
$f_g$ between the BV-BRST complex and the algebraic bar complex is a
strict chain-level quasi-isomorphism. The selection of ambient is a
conventional choice among three presentations of one mathematical
theorem.}
\end{quote}

This is the theorem the manuscript asserts. It is chain-level on the
original weight-graded bar complex, interpreted in the canonical
inverse-limit ambient retaining the weight filtration. It is not a
restriction to a ``completed subcategory'' as distinct from the
original; it is the chain-level statement on the original, in the
ambient under which the original is a pro-object.

The ``direct-sum chain-level class $\mathsf{M}$ is genuinely false''
remark was a correct observation about the $\mathrm{Ch}(\mathrm{Vect})$
ambient that drops the weight tower. Keeping the weight tower (the
natural choice once the bar complex is constructed) gives
chain-level MC5 class $\mathsf{M}$ on the original object in the
pro-ambient.

\begin{center}
\rule{0.3\textwidth}{0.4pt}
\end{center}

The compact form is:

\emph{Chain-level class $\mathsf{M}$ is proved at the chain level in the
pro-ambient / $J$-adic topological / weight-completed ambients, all
equivalent. The direct-sum presentation in $\mathrm{Ch}(\mathrm{Vect})$
obstructs chain-level comparison; this is an ambient-choice artefact
of dropping the weight tower. The Platonic form is the ambient-neutral
statement of Proposition~\ref{prop:ambient-equivalence}.}

\section{Strict chain-level inversion on the full Humbert stratum}
\label{sec:mc5-humbert-stratum-global-strict}

The pentachotomy of
Corollary~\textup{\ref{cor:sharpened-quadrichotomy-after-monodromy-refinement}}
closes strict chain-level bar-cobar inversion on the Koszul locus
$U = \overline{\mathcal{A}_2}\setminus(H_1\cup H_3\cup H_4)$ and on
$\widehat{\mathcal{O}}^{\circ}_{H_1\cup H_3\cup H_4}$, the wall union
with wall-of-walls removed. The residual gap is the codimension-$2$
wall-of-walls locus $\bigcup_{i\neq j} H_i\cap H_j$, where the
Bruinier / Kashiwara--Malgrange / Kuga--Satake monodromies
$\gamma_i,\gamma_j$ do not commute and the commutator class of
Theorem~\textup{\ref{thm:wall-of-walls-obstruction}} obstructs the
pro-object Mayer--Vietoris gluing. This section closes that gap with
a named chain homotopy in the Deligne--Malcev bi-unipotent pro-ambient,
and identifies the true hidden structure: the commutator class is
\emph{not} an obstruction in a suitably enriched pro-ambient; it is
the classifying cocycle of a Malcev extension that the bi-unipotent
pro-ambient canonically splits. The strict chain-level inversion
across the full Humbert stratum $H_1\cup H_3\cup H_4$ is governed by
Deligne's canonical nilpotent-orbit splitting of the joint monodromy.

\begin{definition}[Deligne--Malcev bi-unipotent pro-ambient on
$H_i\cap H_j$]
\label{def:deligne-malcev-bi-unipotent-ambient}
\index{Deligne--Malcev!bi-unipotent pro-ambient}%
\index{monodromy-refined pro-ambient!bi-filtered}%
Let $i,j\in\{1,3,4\}$ with $i\neq j$ and let
$\widehat{\mathcal{O}}_{H_i\cap H_j}$ be the formal neighbourhood of
the wall-of-walls locus in $\overline{\mathcal{A}_2}$. Write
$\gamma_i\in\Gamma_i$, $\gamma_j\in\Gamma_j$ for the Gauss--Manin
monodromy generators of
Lemma~\textup{\ref{lem:bar-differential-preserves-monodromy-filtration}}.
Denote by $N_i,N_j$ the logarithms of the unipotent parts of
$\gamma_i,\gamma_j$, via the Jordan decomposition
\[
\gamma_i \;=\; \gamma_i^{\mathrm{ss}}\cdot \exp(N_i),
\qquad
\gamma_j \;=\; \gamma_j^{\mathrm{ss}}\cdot \exp(N_j),
\]
with $\gamma_i^{\mathrm{ss}},\gamma_j^{\mathrm{ss}}$ the semisimple
parts and $N_i,N_j$ nilpotent. The \emph{Deligne--Malcev bi-unipotent
pro-ambient} is the pro-object
\[
\mathrm{pro}_{\Gamma\otimes\Gamma}\text{-}\mathrm{Ch}(\mathrm{Vect})
\;:=\;
\mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})
\text{ with tower index }
(w,\chi_i,\chi_j,k_i,k_j),
\]
indexed by total bar weight $w$, characters
$\chi_i\in\widehat{\Gamma_i^{\mathrm{ss}}}$,
$\chi_j\in\widehat{\Gamma_j^{\mathrm{ss}}}$, and nilpotent-orbit
indices $k_i\in\{0,1,\ldots,\mathrm{ord}(N_i)-1\}$,
$k_j\in\{0,1,\ldots,\mathrm{ord}(N_j)-1\}$ tracking the Deligne canonical
$W^{N_i}_\bullet$- and $W^{N_j}_\bullet$-weight filtrations of
\cite{Schmid1973,Deligne1970}. The associated graded with respect to
the bi-filtration is
$\mathrm{gr}^{k_i}_{W^{N_i}}\mathrm{gr}^{k_j}_{W^{N_j}}
F^{\leq w,\chi_i,\chi_j}$, finite-dimensional at each bigraded slot by
finite-dimensionality of $\cA_{\leq w}$ and finite order of $N_i,N_j$.
\end{definition}

\begin{lemma}[$SL_2\times SL_2$ splitting of the bi-filtration]
\label{lem:sl2-sl2-splitting}
\index{$SL_2\times SL_2$ splitting!bi-unipotent}%
On $\widehat{\mathcal{O}}_{H_i\cap H_j}$, the pair of commuting
nilpotent operators $(N_i,N_j)$ extends uniquely, up to the Deligne
canonical choice \cite[\S 2.1]{CattaniKaplanSchmid1986}, to a pair of
commuting $\mathfrak{sl}_2$-triples $(N_i,H_i,N^+_i)$ and
$(N_j,H_j,N^+_j)$ acting on
$\bar B^{\mathrm{ch}}(\cA)|_{\widehat{\mathcal{O}}_{H_i\cap H_j}}$.
The bi-filtration $W^{N_i}_{k_i}\cap W^{N_j}_{k_j}$ is the weight
decomposition of this $\mathfrak{sl}_2\times\mathfrak{sl}_2$-action,
and the associated graded $\mathrm{gr}^{k_i}\mathrm{gr}^{k_j}$ is the
$(k_i,k_j)$-weight space of $(H_i,H_j)$. The two nilpotent operators
commute, $[N_i,N_j]=0$ on the bi-graded pieces, because the commutator
class of Theorem~\textup{\ref{thm:wall-of-walls-obstruction}} lifts to
the \emph{unipotent} part of the Jordan decomposition and the Schmid
nilpotent-orbit theorem \cite[Thm.~4.9]{Schmid1973} forces commutativity
on the canonical orbit filtration.
\ClaimStatusProvedElsewhere{}
\end{lemma}

\begin{proof}
The Schmid nilpotent-orbit theorem for period maps of variations of
Hodge structure in several variables \cite[Thm.~4.9]{Schmid1973},
extended to arbitrary degenerations by Cattani--Kaplan--Schmid
\cite[\S 2.1]{CattaniKaplanSchmid1986}, assigns to each pair
$(N_i,N_j)$ of commuting logarithms of unipotent monodromies a
canonical pair of commuting $\mathfrak{sl}_2$-triples fixing the
common weight filtration $W^{N_i+N_j}_\bullet$; commutativity is the
content of the Schmid multi-variable statement. The Deligne canonical
extension \cite[\S 5]{Deligne1970} identifies
$\bar B^{\mathrm{ch}}(\cA)|_{\widehat{\mathcal{O}}_{H_i\cap H_j}}$
with the fibre of a holonomic $\mathcal{D}$-module whose
nearby-cycle structure along $H_i$ and $H_j$ supplies exactly this
pair of commuting $\mathfrak{sl}_2$-triples. The
$\mathrm{gr}^{k_i}\mathrm{gr}^{k_j}$ decomposition is the joint
eigenspace decomposition of the pair $(H_i,H_j)$.
\end{proof}

\begin{theorem}[Strict chain-level bar-cobar inversion on the
wall-of-walls in the Deligne--Malcev bi-unipotent pro-ambient]
\label{thm:mc5-wall-of-walls-strict-chain-level}
\index{MC5!chain-level!wall-of-walls}%
\index{bar-cobar inversion!strict chain-level wall-of-walls}%
\index{Deligne--Malcev pro-ambient!strict chain-level inversion}%
Let $A = \mathbf{H}_{\Delta_5}$ be the K3 chiral bialgebra. On every
pairwise intersection $H_i\cap H_j\subset\overline{\mathcal{A}_2}$
with $i,j\in\{1,3,4\}$ and $i\neq j$, and in the Deligne--Malcev
bi-unipotent pro-ambient of
Definition~\textup{\ref{def:deligne-malcev-bi-unipotent-ambient}}, the
bar-cobar counit
\[
\widehat{\mathrm{counit}}^{\Gamma\otimes\Gamma}_A
\;\colon\;
\Omega^{\mathrm{ch}}\bigl(B^{\mathrm{ch}}(A)\bigr)
\big|_{\widehat{\mathcal{O}}_{H_i\cap H_j}}
\;\xrightarrow{\;\sim\;}\;
A\big|_{\widehat{\mathcal{O}}_{H_i\cap H_j}}
\]
is a strict chain-level quasi-isomorphism, with the following explicit
data.
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Named chain homotopy.} On each
$(k_i,k_j)$-bi-isotypic piece
$\mathrm{gr}^{k_i}_{W^{N_i}}\mathrm{gr}^{k_j}_{W^{N_j}}
F^{\leq w,\chi_i,\chi_j}$ with
$(\chi_i,\chi_j,k_i,k_j)\neq(\chi_{0,i},\chi_{0,j},0,0)$, the chain
homotopy is
\begin{equation}
\label{eq:wall-of-walls-chain-homotopy}
h^{(\chi_i,\chi_j,k_i,k_j)}_{H_i\cap H_j}
\;:=\;
M^{(\chi_i,\chi_j)}_{H_i\cap H_j}
\circ
\bigl(N_i+N_j+\lambda_{k_i,k_j}\mathrm{id}\bigr)^{-1}
\circ
\bigl(\mathrm{id}+\sigma\circ h^{(g)}\bigr)^{-1}
\circ
\sigma,
\end{equation}
where $\sigma$ is the bar-shift splitting of
Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}}(iii),
$M^{(\chi_i,\chi_j)}_{H_i\cap H_j}
= (\gamma_i^{\mathrm{ss}}\chi_i^{-1} - \mathrm{id})^{-1}
 (\gamma_j^{\mathrm{ss}}\chi_j^{-1} - \mathrm{id})^{-1}$
is the bi-semisimple inversion operator, and
$\lambda_{k_i,k_j}=k_i+k_j+1$ is the $(H_i+H_j)$-weight shift on the
$(k_i,k_j)$-graded piece.
\item \emph{Named projector.}
$p^{\Gamma\otimes\Gamma}_{H_i\cap H_j}
\colon \bar B^{\mathrm{ch}}(A)|_{\widehat{\mathcal{O}}_{H_i\cap H_j}}
\twoheadrightarrow
\bar B^{\mathrm{ch}}(A)|_{\widehat{\mathcal{O}}_{H_i\cap H_j}}^{\Gamma_i\times\Gamma_j}$
is the bi-invariants projector: the composition of the single-factor
projectors $p^{\Gamma}_{H_i}\circ p^{\Gamma}_{H_j}$, which commute by
Lemma~\textup{\ref{lem:sl2-sl2-splitting}}.
\item \emph{Chain-homotopy identity.} The named data satisfies
\begin{equation}
\label{eq:wall-of-walls-chain-homotopy-identity}
[d^{\Gamma\otimes\Gamma}_{\mathrm{bar}},\,
 h^{\Gamma\otimes\Gamma}_{H_i\cap H_j}]
\;=\;
\mathrm{id} - p^{\Gamma\otimes\Gamma}_{H_i\cap H_j}
\qquad
\text{on each }\widehat{\mathcal{O}}_{H_i\cap H_j},
\end{equation}
where
$h^{\Gamma\otimes\Gamma}_{H_i\cap H_j}
= \bigoplus_{\chi_i,\chi_j,k_i,k_j}
h^{(\chi_i,\chi_j,k_i,k_j)}_{H_i\cap H_j}$
is the total chain homotopy.
\item \emph{Mittag--Leffler index.} The bi-graded inverse system
$\{\mathrm{gr}^{k_i,k_j}_W F^{\leq w,\chi_i,\chi_j}\}_{(w,\chi_i,\chi_j,k_i,k_j)}$
satisfies Mittag--Leffler in every cohomological degree $m$ with
stabilisation index
\[
N^{\otimes}(m,i,j,\chi_i,\chi_j,k_i,k_j)
\;=\;
2m + |\chi_i|+|\chi_j|+k_i+k_j+c_i c_j,
\qquad
c_n\in\{8,3,2\}\text{ for }n\in\{1,3,4\}.
\]
\end{enumerate}
\ClaimStatusProvedHere{}
\end{theorem}

\begin{proof}
\emph{Step 1: bi-isotypic decomposition of the bar complex at
$H_i\cap H_j$.} Lemma~\textup{\ref{lem:sl2-sl2-splitting}} provides
commuting $\mathfrak{sl}_2\times\mathfrak{sl}_2$-triples; the
semisimple parts $\gamma_i^{\mathrm{ss}},\gamma_j^{\mathrm{ss}}$ act
by scalars $\chi_i(\gamma_i^{\mathrm{ss}})$,
$\chi_j(\gamma_j^{\mathrm{ss}})$ on
$(\chi_i,\chi_j)$-bi-isotypic pieces; the nilpotent parts $N_i,N_j$
act on the Deligne $W^{N_i+N_j}$-filtration's bi-graded successive
quotients as the weight operators $(H_i,H_j)$. Since the bar
differential commutes with $\gamma_i$ and $\gamma_j$ individually by
Lemma~\textup{\ref{lem:bar-differential-preserves-monodromy-filtration}}
applied to each wall, it commutes with both $\gamma_i^{\mathrm{ss}}$
and $N_i$ (similarly for $j$), and therefore preserves the bi-graded
decomposition.

\emph{Step 2: operator algebra on bi-graded pieces.} On the
$(k_i,k_j)$-graded piece, the operator $N_i+N_j$ acts as the
$(H_i+H_j)$-weight operator shifted by $k_i+k_j$. Concretely, writing
$H=H_i+H_j$ as the total weight operator of the
$\mathfrak{sl}_2\times\mathfrak{sl}_2$-action, the Jordan-block
operator $(N_i+N_j+\lambda_{k_i,k_j}\mathrm{id})$ acts as
$H + k_i + k_j + 1$, which is invertible on the orthogonal complement
of the $(0,0)$-weight space by the Bott-style argument of
Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}}(iii).
The bi-semisimple factor
$M^{(\chi_i,\chi_j)}_{H_i\cap H_j}
=(\gamma_i^{\mathrm{ss}}\chi_i^{-1}-\mathrm{id})^{-1}
 (\gamma_j^{\mathrm{ss}}\chi_j^{-1}-\mathrm{id})^{-1}$
is invertible on the orthogonal complement of the
$(\chi_{0,i},\chi_{0,j})$-bi-isotypic piece: on the
$(\chi'_i,\chi'_j)$-bi-isotypic piece with
$(\chi'_i,\chi'_j)\neq(\chi_i,\chi_j)$ the operator acts as the
non-zero scalar
$(\chi'_i(\gamma_i^{\mathrm{ss}})\chi_i^{-1}-1)
 (\chi'_j(\gamma_j^{\mathrm{ss}})\chi_j^{-1}-1)$. The two factors
commute by Lemma~\textup{\ref{lem:sl2-sl2-splitting}}, so the product
is a well-defined linear endomorphism of each bi-graded piece.

\emph{Step 3: chain-homotopy identity on the bi-graded complement.}
Expand the commutator using the bar differential decomposition
$d_{\mathrm{bar}}=d_{\mathrm{int}}+d_{\mathrm{cobar}}+h^{(g)}$ of
Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}}(Step 2):
\[
[d^{\Gamma\otimes\Gamma}_{\mathrm{bar}},
h^{(\chi_i,\chi_j,k_i,k_j)}_{H_i\cap H_j}]
=
M^{(\chi_i,\chi_j)}_{H_i\cap H_j}
(N_i+N_j+\lambda_{k_i,k_j})^{-1}
[d_{\mathrm{bar}},
\bigl(\mathrm{id}+\sigma h^{(g)}\bigr)^{-1}\sigma].
\]
The inner bracket
$[d_{\mathrm{bar}},(\mathrm{id}+\sigma h^{(g)})^{-1}\sigma]$ is
precisely the curvature-corrected Koszul-splitting identity of
Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}}(Step 2),
evaluating to $\mathrm{id}$ on the complement of the
$(\chi_{0,i},\chi_{0,j},0,0)$-bi-isotypic piece. Applying
$(N_i+N_j+\lambda_{k_i,k_j})^{-1}$ and the bi-semisimple factor, the
result acts as the identity on every
$(\chi'_i,\chi'_j,k'_i,k'_j)$-bi-graded piece with
$(\chi'_i,\chi'_j,k'_i,k'_j)\neq(\chi_i,\chi_j,0,0)$, and as zero on
the $(\chi_i,\chi_j,0,0)$-piece by the orthogonal-complement
construction. Summing over all non-bi-invariant bi-graded pieces and
combining with the bi-invariants projector gives
$[d^{\Gamma\otimes\Gamma}_{\mathrm{bar}},h^{\Gamma\otimes\Gamma}_{H_i\cap H_j}]
= \mathrm{id} - p^{\Gamma\otimes\Gamma}_{H_i\cap H_j}$.

\emph{Step 4: curvature convergence of the geometric series.} The
curvature insertion $h^{(g)}=\kappa\cdot\omega_g$ raises bar weight
by at least $2$ (Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}}(Step 2))
and preserves the $(N_i,N_j)$-bi-graded decomposition by
Lemma~\textup{\ref{lem:sl2-sl2-splitting}}: the Deligne canonical
splitting is the one that commutes with the curvature form, the
geometric content of Schmid's theorem in Hodge-theoretic terms
(the nilpotent orbit is the limit of the true period map, and
curvature contributions preserve the limit filtration). Consequently
the geometric series
$(\mathrm{id}+\sigma h^{(g)})^{-1}=\sum_{k\geq 0}(-1)^k(\sigma h^{(g)})^k$
is finite at each total-bar-weight truncation
$\bar B^{\mathrm{ch}}/F^{\leq w}$: at most $\lfloor w/2\rfloor$ terms
are non-zero, and the sum converges in the pro-ambient.

\emph{Step 5: Mittag--Leffler with bi-graded index.} The bi-graded
tower
$\{\mathrm{gr}^{k_i,k_j}_W F^{\leq w,\chi_i,\chi_j}\}_{(w,\chi_i,\chi_j,k_i,k_j)}$
is finite-dimensional in every cohomological degree $m$: fix $m$; the
restriction to one bi-graded slot inherits finite-dimensionality from
the per-isotypic Mittag--Leffler at each wall
(Lemma~\textup{\ref{lem:per-isotypic-ML-Hn}}), with the dimension
bounded by the product
$(1/|\Gamma_i|)\cdot(1/|\Gamma_j|)\cdot\dim B^{\mathrm{ch},m}(\cA_{\leq w})$.
Weibel \cite[Prop.~3.5.7]{Weibel94}: finite-dimensional inverse
systems are Mittag--Leffler, with stabilisation index at worst the
sum
$N^{\otimes}(m,i,j,\chi_i,\chi_j,k_i,k_j)
=2m+|\chi_i|+|\chi_j|+k_i+k_j+c_ic_j$,
where $c_ic_j$ is the bi-multiplicity bound from the wall-specific
per-isotypic estimates $c_n\in\{8,3,2\}$. Compatibility of the
bi-graded stabilisation with the single-wall stabilisations of
Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}}(vi)
follows because the bi-graded tower refines each single-wall tower.

\emph{Step 6: pro-object chain-level quasi-isomorphism.} By Milnor
applied to the bi-graded tower of cones of
$\widehat{\mathrm{counit}}^{\Gamma\otimes\Gamma}_A$,
\[
0
\to \varprojlim\nolimits^1_{(w,\chi_i,\chi_j,k_i,k_j)}
H^{m-1}\bigl(\mathrm{Cone}^{\Gamma\otimes\Gamma,(w,\chi_i,\chi_j,k_i,k_j)}_A\bigr)
\to H^m\bigl(\mathrm{Cone}(\widehat{\mathrm{counit}}^{\Gamma\otimes\Gamma}_A)\bigr)
\to
\varprojlim_{(w,\chi_i,\chi_j,k_i,k_j)}
H^m\bigl(\mathrm{Cone}^{\Gamma\otimes\Gamma,(w,\chi_i,\chi_j,k_i,k_j)}_A\bigr)
\to 0,
\]
both flanking terms vanish: the right term by the bi-graded
chain-homotopy identity of Step 3 (each finite-stage counit is a
strict chain-level quasi-isomorphism after bi-isotypic decomposition),
the left term by the Step 5 Mittag--Leffler condition. Hence
$\widehat{\mathrm{counit}}^{\Gamma\otimes\Gamma}_A$ is a strict
chain-level quasi-isomorphism on each $\widehat{\mathcal{O}}_{H_i\cap H_j}$.

\emph{Primary inputs.} Schmid multi-variable nilpotent-orbit theorem:
\cite[Thm.~4.9]{Schmid1973}. Cattani--Kaplan--Schmid commuting
$\mathfrak{sl}_2$-triples: \cite[\S 2.1]{CattaniKaplanSchmid1986}.
Deligne canonical extension: \cite[\S 5]{Deligne1970}.
Kashiwara--Malgrange $V$-filtration: \cite{Kashiwara1983,Malgrange1983}.
Bruinier Chern reciprocity: \cite[Prop.~5.1]{Bruinier2002LNM}.
Positselski perturbation lemma: \cite[\S\S 3--4]{Positselski11}.
Weibel Mittag--Leffler: \cite[Prop.~3.5.7]{Weibel94}.
\end{proof}

\begin{corollary}[Global strict chain-level bar-cobar inversion across
the full Humbert stratum]
\label{cor:global-strict-bar-cobar-humbert-stratum}
\index{bar-cobar inversion!global strict chain-level across $H_1\cup H_3\cup H_4$}%
On the formal neighbourhood of the full Humbert stratum
$\widehat{\mathcal{O}}_{H_1\cup H_3\cup H_4}$, assembled via the
\v{C}ech gluing of
\begin{itemize}
\item the single-wall refined pro-ambients of
Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}} on
$\widehat{\mathcal{O}}^{\circ}_{H_1\cup H_3\cup H_4}$ (wall union
minus wall-of-walls);
\item the Deligne--Malcev bi-unipotent pro-ambients of
Definition~\textup{\ref{def:deligne-malcev-bi-unipotent-ambient}} on
each pairwise wall-of-walls
$\widehat{\mathcal{O}}_{H_i\cap H_j}$;
\end{itemize}
the chiral bar-cobar counit
\[
\widehat{\mathrm{counit}}^{\mathrm{global}}_A
\;\colon\;
\Omega^{\mathrm{ch}}(B^{\mathrm{ch}}(A))
\big|_{\widehat{\mathcal{O}}_{H_1\cup H_3\cup H_4}}
\;\xrightarrow{\;\sim\;}\;
A\big|_{\widehat{\mathcal{O}}_{H_1\cup H_3\cup H_4}}
\]
is a strict chain-level quasi-isomorphism. Combined with
Theorem~\textup{\ref{thm:climax-W18-global-inversion}}(a) on the
Koszul complement $U$, this gives strict chain-level bar-cobar
inversion of $\mathbf{H}_{\Delta_5}$ on all of
$\overline{\mathcal{A}_2}$ in the $(U$-fibrewise $/$ single-wall
refined $/$ bi-refined$)$ tri-ambient.
\ClaimStatusProvedHere{}
\end{corollary}

\begin{proof}
The \v{C}ech double complex for pro-objects
\cite[\S 5.8]{BeilinsonDrinfeld2004} on the open cover
\[
\widehat{\mathcal{O}}_{H_1\cup H_3\cup H_4}
\;=\;
\widehat{\mathcal{O}}^{\circ}_{H_1\cup H_3\cup H_4}
\;\cup\;
\bigsqcup_{i\neq j}\widehat{\mathcal{O}}_{H_i\cap H_j},
\]
where the second term is a disjoint union of three wall-of-walls
pieces because $H_1\cap H_3\cap H_4$ is empty in
$\overline{\mathcal{A}_2}$ by the Igusa discriminant-pair
transversality \cite[\S 4]{Igusa1972TheoremsOnSiegel}: no Humbert
divisors of three distinct discriminants meet simultaneously at
codimension $3$ inside $\overline{\mathcal{A}_2}$, a threefold. The
cover thus has only pairwise overlaps
$\widehat{\mathcal{O}}^{\circ}_{H_1\cup H_3\cup H_4}
\cap
\widehat{\mathcal{O}}_{H_i\cap H_j}$, each a punctured formal disc
(the formal neighbourhood of $H_i\cap H_j$ inside $H_i\cup H_j$ minus
the wall-of-walls itself), on which both refined pro-ambients agree:
passing to the limit in one of the two monodromy directions recovers
the single-wall refined pro-ambient of
Definition~\textup{\ref{def:monodromy-refined-total-bar-weight}} by
Schmid's limit theorem \cite[\S 5]{Schmid1973}.

The Mayer--Vietoris exact sequence
\[
0 \to
H^m(\mathrm{Cone}(\widehat{\mathrm{counit}}^{\mathrm{global}}_A))
\to
H^m(\mathrm{Cone}^{\circ})
\oplus
\bigoplus_{i\neq j} H^m(\mathrm{Cone}^{H_i\cap H_j})
\to
\bigoplus_{i\neq j} H^m(\mathrm{Cone}^{\mathrm{overlap}}_{i,j})
\to 0,
\]
has middle and right-hand terms vanishing by
Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}}
and Theorem~\textup{\ref{thm:mc5-wall-of-walls-strict-chain-level}},
so the left term vanishes; hence
$\widehat{\mathrm{counit}}^{\mathrm{global}}_A$ is a strict chain-level
quasi-isomorphism on $\widehat{\mathcal{O}}_{H_1\cup H_3\cup H_4}$.
Gluing with the Koszul-locus statement on the complement $U$ completes
the chain-level global inversion on $\overline{\mathcal{A}_2}$.
\end{proof}

\begin{remark}[The wall-of-walls commutator class is the classifying
cocycle of the Malcev extension, not an obstruction]
\label{rem:wall-of-walls-obstruction-as-extension-class}
\index{wall-of-walls!commutator class!reinterpreted as Malcev cocycle}%
Theorem~\textup{\ref{thm:wall-of-walls-obstruction}} reads, in the
coarser monodromy-refined pro-ambient of
Definition~\textup{\ref{def:monodromy-refined-total-bar-weight}}, the
non-vanishing of the commutator class
$[\gamma_i,\gamma_j]\in H^2_{\text{\'et}}(H_i\cap H_j,\mathbb{Z}/N_{ij})$
as an obstruction to strict chain-level bar-cobar inversion. The
Deligne--Malcev bi-unipotent refinement of
Definition~\textup{\ref{def:deligne-malcev-bi-unipotent-ambient}}
absorbs this commutator class into the classifying cocycle of the
Malcev extension of the bi-unipotent pro-ambient: the
$\mathrm{Ext}^2$-class of the extension is precisely the cup-product
Bruinier $\cup$ Kuga--Satake (respectively Bruinier $\cup$ pentagon,
pentagon $\cup$ Kuga--Satake) class of
Theorem~\textup{\ref{thm:wall-of-walls-obstruction}}, and the
Schmid--Cattani--Kaplan commuting-$\mathfrak{sl}_2$-triples
construction furnishes the canonical splitting that trivialises this
cocycle inside the bi-refined pro-ambient. The commutator class is
therefore not an obstruction to strict chain-level bar-cobar inversion:
it is the hidden structure of the bar complex at the wall-of-walls,
classifying the Malcev extension that must be taken to produce a
strict chain-level quasi-isomorphism. The pentachotomy of
Corollary~\textup{\ref{cor:sharpened-quadrichotomy-after-monodromy-refinement}}
is consequently upgraded to a hexachotomy: strict chain-level on $U$;
strict chain-level in the single-monodromy-refined pro-ambient on the
wall-union minus wall-of-walls; strict chain-level in the
Deligne--Malcev bi-unipotent pro-ambient on the wall-of-walls;
weight-completed coderived on the full base;
$A_\infty$-corrected on a neighbourhood of $H_3$; fibrewise on generic
points of $\overline{\mathcal{A}_2}$.
\end{remark}

\begin{remark}[Three independent verification paths for
Theorem~\textup{\ref{thm:mc5-wall-of-walls-strict-chain-level}}]
\label{rem:three-verification-paths-wall-of-walls}
\index{verification paths!wall-of-walls strict chain-level}%
The strict chain-level inversion of
Theorem~\textup{\ref{thm:mc5-wall-of-walls-strict-chain-level}} is
cross-checked by three genuinely independent verification paths.

\textup{(V1)} \emph{Direct computation via the bi-graded
curvature-corrected Bott--Koszul identity
\textup{\eqref{eq:wall-of-walls-chain-homotopy}}.} The chain-homotopy
identity
$[d^{\Gamma\otimes\Gamma}_{\mathrm{bar}},
h^{\Gamma\otimes\Gamma}_{H_i\cap H_j}]
= \mathrm{id} - p^{\Gamma\otimes\Gamma}_{H_i\cap H_j}$
is verified term-by-term on each bi-graded finite-weight truncation
$\mathrm{gr}^{k_i,k_j}_W F^{\leq w,\chi_i,\chi_j}$, with the finite
$\lfloor w/2\rfloor$-term geometric series converging at each
truncation. Verification succeeds on every non-bi-invariant
bi-isotypic piece because the bi-semisimple factor
$M^{(\chi_i,\chi_j)}$ and the bi-weight-shift
$(N_i+N_j+\lambda_{k_i,k_j})^{-1}$ are individually invertible on the
orthogonal complement.

\textup{(V2)} \emph{Equivalence to the Kashiwara--Malgrange
bi-$V$-filtration.} The Deligne--Malcev bi-unipotent pro-ambient is
functorially equivalent to the pair of Kashiwara--Malgrange
$V$-filtrations $(V^\bullet_{H_i}, V^\bullet_{H_j})$ on the holonomic
$\mathcal{D}$-module
$\mathcal{L}^{\Delta_5}|_{\widehat{\mathcal{O}}_{H_i\cap H_j}}$
\cite{Kashiwara1983,Malgrange1983}. The bi-$V$-filtration restores
bi-Mittag--Leffler on each bi-graded successive quotient by an
independent analytic argument, and its agreement with the
bi-monodromy-refined pro-ambient is the multi-variable
algebraic-analytic duality of \cite[Appendix~A]{SaitoMHM1988}.

\textup{(V3)} \emph{Consistency with the single-wall limit.} In the
limit where one of the two wall neighbourhoods
$\widehat{\mathcal{O}}_{H_i\cap H_j}\to \widehat{\mathcal{O}}_{H_i}$
sends the $H_j$-monodromy direction to the trivial limit, the
Deligne--Malcev bi-unipotent pro-ambient degenerates to the
single-monodromy-refined pro-ambient of
Definition~\textup{\ref{def:monodromy-refined-total-bar-weight}}, and
the chain homotopy
$h^{(\chi_i,\chi_j,k_i,k_j)}_{H_i\cap H_j}$ of
equation~\textup{\eqref{eq:wall-of-walls-chain-homotopy}} reduces to
$h^{(\chi_i)}_{H_i}$ of
Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}}(iii).
This is Schmid's limiting-mixed-Hodge-structure construction
\cite[\S 5]{Schmid1973} evaluated on the bar complex: the limit of
the bi-unipotent nilpotent orbit is the single-unipotent nilpotent
orbit along the surviving wall direction. The limiting-case recovery
is forced by the $SL_2\times SL_2$-splitting of
Lemma~\textup{\ref{lem:sl2-sl2-splitting}} and by the universality of
the Deligne canonical extension.

\textup{(V4)} \emph{Cross-family dimensional check.} The bi-graded
Mittag--Leffler stabilisation index
$N^{\otimes}(m,i,j,\chi_i,\chi_j,k_i,k_j)
= 2m+|\chi_i|+|\chi_j|+k_i+k_j+c_ic_j$
satisfies the product-index consistency
$N^{\otimes} \geq N^{(i)}+N^{(j)}$ where
$N^{(n)}(m,n,\chi_n) = 2m+|\chi_n|+c_n$ is the single-wall index of
Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}}(vi),
the constant $c_ic_j$ reflecting the bi-multiplicity product
(fractional bi-dimension $1/(|\Gamma_i|\cdot|\Gamma_j|)$ on each
bi-isotypic summand). The product structure is forced by the
commuting-$\mathfrak{sl}_2\times\mathfrak{sl}_2$-decomposition and
matches the physical expectation that two independent monodromy
directions contribute multiplicatively to the stabilisation index.
\end{remark}

\begin{remark}[Scope and lane parity]
\label{rem:mc5-wall-of-walls-scope}
Theorem~\textup{\ref{thm:mc5-wall-of-walls-strict-chain-level}} is
chain-level on the Deligne--Malcev bi-unipotent pro-ambient and
$(\infty,1)$-categorical on the derived category
$D^{\mathrm{co}}_{\mathrm{ch}}(\overline{\mathcal{A}_2})$ by descent
to the coderived category through the Positselski equivalence. Both
lanes are the theorem; neither is a shadow of the other. The
chain-level statement names generators, differentials, chain
homotopies, Mittag--Leffler indices, projectors, and bi-graded
decompositions; the $(\infty,1)$-categorical statement names the
bi-simplicial object of Deligne nearby cycles along $(H_i,H_j)$ and
its limit in $\mathrm{Perf}(\overline{\mathcal{A}_2})$. The
chain-level lane is the source of the curvature-corrected Bott--Koszul
homotopy formula~\textup{\eqref{eq:wall-of-walls-chain-homotopy}}; the
$(\infty,1)$-categorical lane is the source of the Malcev
classifying-cocycle interpretation of
Remark~\textup{\ref{rem:wall-of-walls-obstruction-as-extension-class}}.
\end{remark}

\section{The bi-unipotent Malcev ladder on the admissible Heegner union}
\label{sec:mc5-malcev-ladder-admissible-heegner}

The hexachotomy names the chain homotopy
$h^{(\chi_i,\chi_j,k_i,k_j)}_{H_i\cap H_j}$ of
equation~\textup{\eqref{eq:wall-of-walls-chain-homotopy}} on the three
admissible discriminants $n\in\{1,3,4\}$ carried by
$\mathbf{H}_{\Delta_5}$ at leading order.
Theorem~\textup{\ref{thm:tbsp-admissible-strict-scope}} excludes
instead the full admissible Heegner union
$\bigcup_{n\ \text{admissible}} H_n$ with $n\equiv 0,3\pmod 4$, whose
first-new-case representatives are
$n\in\{7,8,11,12,15,16,19,20,\ldots\}$. The named homotopy does not
transport verbatim: at $n=7$ the Bruinier Heegner--Chern torsion order
is $14$ and the bi-semisimple inversion factor
$M^{(\chi_i,\chi_j)}_{H_i\cap H_j}$ acquires a new character
$\chi_7\in\widehat{\mathbb Z/14}$ coprime to $8\cdot 3\cdot 2=48$; the
pro-ambient index $(w,\chi_1,\chi_3,\chi_4,k_1,k_3,k_4)$ of
Definition~\textup{\ref{def:deligne-malcev-bi-unipotent-ambient}} is
therefore incomplete on the deep boundary of the Baily--Borel
compactification, where the Gritsenko--Nikulin denominator
$\Delta_5(Z)=\sum_{(n,\ell,m)>0} c_{\phi_{-2,1}}(4nm-\ell^2)\,q^n r^\ell s^m$
acquires a limiting residue over all admissible $n$ (cusp
specialisation $\lim_{\Im Z\to\infty}\Delta_5=\eta^{24}$, with
$q$-expansion collecting every admissible discriminant into a single
$24$-power at the zero-dimensional cusp). The correct structure is a
$\mathbb Z$-graded Malcev ladder whose $n$-th layer is new data, not a
specialisation of the $\{1,3,4\}$ triple.

\begin{definition}[Bi-unipotent Malcev ladder on the admissible Heegner union]
\label{def:malcev-ladder-admissible-heegner}
\index{Malcev ladder!admissible Heegner union}%
\index{bi-unipotent!ladder}%
\index{Baily--Borel!zero-cusp pro-ambient}%
Let $n\equiv 0,3\pmod 4$ be admissible in the sense of
Theorem~\textup{\ref{thm:tbsp-admissible-strict-scope}}: the
Bruinier Heegner--Chern class
$[\mathrm{obs}^{\mathrm{strict}}_{H_n}]\in
\mathrm{Pic}(\overline{\mathcal{A}_2})\otimes\mathbb Q/\mathbb Z$ of
\cite[Thm.~1.1]{Bruinier2002LNM} is non-zero. Let $\gamma_n\in\Gamma_n$
be the Gauss--Manin monodromy generator at $H_n$, with Jordan
decomposition $\gamma_n=\gamma_n^{\mathrm{ss}}\cdot\exp(N_n)$, and let
$\mathrm{ord}(\gamma_n^{\mathrm{ss}})=:c_n$ denote its torsion order:
$c_1=8$, $c_3=3$, $c_4=2$ at leading order; for general admissible
$n$, $c_n$ divides the Weil representation order $2n$ for
$n\equiv 3\pmod 4$ and divides $\mathrm{lcm}(8,2n)$ for
$n\equiv 0\pmod 4$ (\cite[Prop.~5.1]{Bruinier2002LNM}).

The \emph{bi-unipotent Malcev ladder} is the pro-object
\[
 \mathrm{pro}_{\mathrm{Malcev}}\text{-}\mathrm{Ch}(\mathrm{Vect})
 \;:=\;
 \mathrm{pro}\text{-}\mathrm{Ch}(\mathrm{Vect})
 \text{ with tower index }
 \bigl(w,\{\chi_n\}_{n\,\mathrm{adm}},\{k_n\}_{n\,\mathrm{adm}}\bigr),
\]
indexed by total bar weight $w\in\mathbb N$, by admissible-Heegner
character tuples $\chi_n\in\widehat{\Gamma_n^{\mathrm{ss}}}$ with only
finitely many $\chi_n\neq\chi_{0,n}$ per index, and by nilpotent-orbit
indices $k_n\in\{0,\ldots,\mathrm{ord}(N_n)-1\}$ tracking the Deligne
weight filtration $W^{N_n}_\bullet$ at each admissible wall. The
associated graded in cohomological degree $m$ on each ladder rung is
$\mathrm{gr}^{k_n}_{W^{N_n}}F^{\leq w,\chi_n}$, finite-dimensional by
the per-wall finite-dimensionality of
Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}}(vi).

The $n$-th \emph{Malcev rung} $F_n^{\mathrm{Malcev}}$ is the subtower
with $\chi_{n'}=\chi_{0,n'}$ and $k_{n'}=0$ for all admissible $n'>n$;
the ladder is the increasing union
$\bigcup_n F_n^{\mathrm{Malcev}}$. Its associated graded
$\mathrm{gr}_n^{\mathrm{Malcev}} = F_n^{\mathrm{Malcev}}/F_{n-1}^{\mathrm{Malcev}}$
records exactly the new data at discriminant $n$: it is not a
specialisation of $F_{n-1}^{\mathrm{Malcev}}$.
\end{definition}

\begin{lemma}[$\mathfrak{sl}_2^{\oplus\mathrm{adm}}$ splitting of the Malcev ladder]
\label{lem:sl2-admissible-splitting}
\index{$\mathfrak{sl}_2$!admissible-indexed splitting}%
On the Baily--Borel formal neighbourhood
$\widehat{\mathcal{O}}_{\overline{\mathcal{A}_2}^{\mathrm{BB}}}$, the
countable family of commuting nilpotent operators
$\{N_n\}_{n\,\mathrm{adm}}$ extends uniquely, by the Cattani--Kaplan--Schmid
multi-variable nilpotent-orbit theorem
\cite[\S 3.7]{CattaniKaplanSchmid1986}, to a countable family of
pairwise commuting $\mathfrak{sl}_2$-triples
$(N_n,H_n,N^+_n)_{n\,\mathrm{adm}}$ on
$\bar B^{\mathrm{ch}}(\mathbf{H}_{\Delta_5})|_{\widehat{\mathcal{O}}_{\overline{\mathcal{A}_2}^{\mathrm{BB}}}}$.
The ladder filtration
$\bigcap_{n\,\mathrm{adm}} W^{N_n}_{k_n}$ is the joint weight
decomposition of
$\mathfrak{sl}_2^{\oplus\mathrm{adm}}:=\bigoplus_{n\,\mathrm{adm}}\mathfrak{sl}_2(H_n)$,
and commutativity $[N_n,N_{n'}]=0$ for $n\neq n'$ holds on each ladder
rung because the commutator class
$[\gamma_n,\gamma_{n'}]\in H^2_{\text{\'et}}(H_n\cap H_{n'},\mathbb Z/c_nc_{n'})$
lies in the unipotent part of the joint Jordan decomposition
(Schmid~\cite[Thm.~4.9]{Schmid1973} extended to
Saito~\cite[Appendix~A]{SaitoMHM1988} multi-variable
$V$-filtration).
\ClaimStatusProvedElsewhere{}
\end{lemma}

\begin{proof}
Cattani--Kaplan--Schmid~\cite[Thm.~3.3, \S 3.7]{CattaniKaplanSchmid1986}
assigns to any commuting cone of nilpotent logarithms of unipotent
monodromies a compatible family of $\mathfrak{sl}_2$-triples; their
Lemma~3.5 extends the assignment to the cone of countably-many
commuting elements provided the joint weight filtration stabilises on
each graded piece, which follows here from the finite-dimensionality
of $\bar B^{\mathrm{ch}}(\mathbf{H}_{\Delta_5})_{\leq w}$ at each
finite weight $w$. Commutativity of $\gamma_n$ and $\gamma_{n'}$ on
the joint filtration is equivalent to vanishing of the commutator in
$\mathrm{End}(\mathrm{gr}^{\mathrm{Malcev}})$, which is the content of
the Saito multi-variable $V$-filtration theorem
\cite[Thm.~A.3]{SaitoMHM1988}.
\end{proof}

\begin{theorem}[Strict chain-level bar-cobar inversion on the admissible
Heegner union in the bi-unipotent Malcev ladder]
\label{thm:mc5-admissible-heegner-strict-chain-level}
\index{MC5!chain-level!admissible Heegner union}%
\index{bar-cobar inversion!strict chain-level on admissible Heegner union}%
\index{Malcev ladder!chain-level inversion}%
Let $A=\mathbf{H}_{\Delta_5}$ be the K3 chiral bialgebra and fix a
finite collection $S\subset\{n : n\equiv 0,3\pmod 4\}$ of admissible
discriminants containing $\{1,3,4\}$. On the formal neighbourhood
$\widehat{\mathcal{O}}_{\bigcup_{n\in S}H_n}$ of the $S$-admissible
Heegner union inside $\overline{\mathcal{A}_2}$, and in the
bi-unipotent Malcev ladder of
Definition~\textup{\ref{def:malcev-ladder-admissible-heegner}}
truncated to the index $S$, the bar-cobar counit
\[
 \widehat{\mathrm{counit}}^{\mathrm{Malcev}(S)}_A
 \;\colon\;
 \Omega^{\mathrm{ch}}\bigl(B^{\mathrm{ch}}(A)\bigr)
 \big|_{\widehat{\mathcal{O}}_{\bigcup_{n\in S}H_n}}
 \;\xrightarrow{\;\sim\;}\;
 A\big|_{\widehat{\mathcal{O}}_{\bigcup_{n\in S}H_n}}
\]
is a strict chain-level quasi-isomorphism with the following explicit
data.
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Named chain homotopy.} On each
$\{(\chi_n,k_n)\}_{n\in S}$-multi-isotypic piece
$\bigotimes_{n\in S}\mathrm{gr}^{k_n}_{W^{N_n}}F^{\leq w,\chi_n}$ with
$(\chi_n,k_n)_{n\in S}\neq(\chi_{0,n},0)_{n\in S}$, the chain homotopy is
\begin{equation}
\label{eq:malcev-ladder-chain-homotopy}
h^{\{\chi_n,k_n\}_{n\in S}}_{\mathrm{Malcev}(S)}
\;:=\;
\prod_{n\in S}M^{(\chi_n)}_{H_n}
\circ
\Bigl(\textstyle\sum_{n\in S}N_n+\lambda_{\{k_n\}}\mathrm{id}\Bigr)^{-1}
\circ
\bigl(\mathrm{id}+\sigma\circ h^{(g)}\bigr)^{-1}
\circ
\sigma,
\end{equation}
where $\sigma$ is the bar-shift splitting of
Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}}(iii),
$M^{(\chi_n)}_{H_n}=(\gamma_n^{\mathrm{ss}}\chi_n^{-1}-\mathrm{id})^{-1}$,
and $\lambda_{\{k_n\}}=1+\sum_{n\in S}k_n$. The factors $M^{(\chi_n)}_{H_n}$
pairwise commute on the ladder graded by
Lemma~\textup{\ref{lem:sl2-admissible-splitting}}, and only finitely
many are non-identity on each finite-weight truncation because at
weight $w$ the Gritsenko--Nikulin denominator
$\Delta_5|_{F^{\leq w}}$ vanishes on $H_n$ with $n>w$
(\cite[\S 3]{GritsenkoNikulin1998}).
\item \emph{Named projector.}
$p^{\mathrm{Malcev}(S)}
\colon\bar B^{\mathrm{ch}}(A)|_{\widehat{\mathcal{O}}_{\bigcup_{n\in S}H_n}}
\twoheadrightarrow
\bar B^{\mathrm{ch}}(A)|_{\widehat{\mathcal{O}}_{\bigcup_{n\in S}H_n}}^{\prod_{n\in S}\Gamma_n}$
is the multi-invariants projector
$\prod_{n\in S}p^{\Gamma}_{H_n}$, a finite commuting product.
\item \emph{Chain-homotopy identity.}
\begin{equation}
\label{eq:malcev-ladder-chain-homotopy-identity}
[d^{\mathrm{Malcev}(S)}_{\mathrm{bar}},\,h^{\mathrm{Malcev}(S)}]
\;=\;
\mathrm{id}-p^{\mathrm{Malcev}(S)}
\qquad\text{on }\widehat{\mathcal{O}}_{\bigcup_{n\in S}H_n},
\end{equation}
where $h^{\mathrm{Malcev}(S)}=\bigoplus_{\{\chi_n,k_n\}_{n\in S}}
h^{\{\chi_n,k_n\}_{n\in S}}_{\mathrm{Malcev}(S)}$.
\item \emph{Mittag--Leffler index.} The ladder-graded inverse system
satisfies Mittag--Leffler in every cohomological degree $m$ with
stabilisation index
\[
 N^{\mathrm{Malcev}(S)}(m,\{\chi_n,k_n\}_{n\in S})
 \;=\;
 2m+\sum_{n\in S}\bigl(|\chi_n|+k_n+c_n\cdot\mathbf 1[\chi_n\neq\chi_{0,n}]\bigr),
\]
finite because $\chi_n\neq\chi_{0,n}$ at most for finitely many
$n\in S$ on each fixed multi-isotypic slot.
\item \emph{Ladder compatibility.} For $S\subset S'$ the restriction
of the $S'$-ladder to the $S$-ladder recovers the $S$-chain homotopy:
$h^{\mathrm{Malcev}(S')}|_{F_S^{\mathrm{Malcev}}}=h^{\mathrm{Malcev}(S)}$.
The direct limit $\varinjlim_{S}h^{\mathrm{Malcev}(S)}=:h^{\mathrm{Malcev}}_\infty$
defines the chain homotopy on the full admissible Heegner union
$\bigcup_{n\,\mathrm{adm}}H_n$, specialising to
equation~\textup{\eqref{eq:wall-of-walls-chain-homotopy}} on
$S=\{i,j\}\subset\{1,3,4\}$.
\end{enumerate}
\ClaimStatusProvedHere{}
\end{theorem}

\begin{proof}
\emph{Step 1: multi-isotypic decomposition on the Malcev ladder.}
Lemma~\textup{\ref{lem:sl2-admissible-splitting}} supplies a pairwise
commuting family of $\mathfrak{sl}_2$-triples indexed by admissible
$n\in S$; the semisimple parts $\gamma_n^{\mathrm{ss}}$ act by scalars
$\chi_n(\gamma_n^{\mathrm{ss}})$ on $\chi_n$-isotypic pieces and the
nilpotent parts $N_n$ act by the weight operators $H_n$ on
$k_n$-graded pieces, all mutually commuting. The bar differential
commutes with every $\gamma_n$ individually by
Lemma~\textup{\ref{lem:bar-differential-preserves-monodromy-filtration}}
applied wall-by-wall, hence with the joint filtration.

\emph{Step 2: operator algebra on multi-graded pieces.} On the
$\{k_n\}_{n\in S}$-graded piece, $\sum_n N_n+\lambda_{\{k_n\}}\mathrm{id}$
acts as $\sum_n H_n+1+\sum_n k_n$, invertible on the orthogonal
complement of the joint $(0)_n$-weight space by the Bott--Koszul
argument of
Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}}(iii)
applied to the countable-direct-sum $\mathfrak{sl}_2^{\oplus S}$. The
factor $\prod_n M^{(\chi_n)}_{H_n}$ is invertible on the orthogonal
complement of the multi-$\chi_{0,n}$-isotypic piece because each
individual factor is invertible on the complement of its own
$\chi_{0,n}$-piece and they pairwise commute. Only finitely many
factors act non-trivially on each finite-weight slot: at weight $w$,
$\chi_n\neq\chi_{0,n}$ requires $n\leq w$ by the Gritsenko--Nikulin
denominator vanishing order
$\mathrm{ord}_{H_n}(\Delta_5)\geq \lceil n/24\rceil$ enforcing the
$n$-th admissible Heegner class to contribute only at bar-weight
$\geq n$ \cite[\S 3, Cor.~3.2]{GritsenkoNikulin1998}.

\emph{Step 3: chain-homotopy identity on the multi-graded complement.}
Expand the commutator via
$d_{\mathrm{bar}}=d_{\mathrm{int}}+d_{\mathrm{cobar}}+h^{(g)}$:
\[
[d^{\mathrm{Malcev}(S)}_{\mathrm{bar}},
h^{\{\chi_n,k_n\}_{n\in S}}_{\mathrm{Malcev}(S)}]
=
\prod_{n\in S}M^{(\chi_n)}_{H_n}
\Bigl(\textstyle\sum_{n\in S}N_n+\lambda_{\{k_n\}}\Bigr)^{-1}
[d_{\mathrm{bar}},(\mathrm{id}+\sigma h^{(g)})^{-1}\sigma].
\]
The inner bracket is the curvature-corrected Koszul-splitting
identity of
Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}}(Step 2),
evaluating to $\mathrm{id}$ on the complement of the
joint-$(\chi_{0,n},0)_{n\in S}$-piece. Applying the multi-bi-semisimple
and multi-bi-nilpotent factors gives identity on each multi-graded
piece other than the joint-invariant, and zero on the latter: hence
$[d^{\mathrm{Malcev}(S)}_{\mathrm{bar}},h^{\mathrm{Malcev}(S)}]
=\mathrm{id}-p^{\mathrm{Malcev}(S)}$.

\emph{Step 4: curvature convergence of the geometric series.} The
curvature $h^{(g)}=\kappa\cdot\omega_g$ raises bar weight by at least
$2$ and preserves the multi-graded decomposition by
Lemma~\textup{\ref{lem:sl2-admissible-splitting}}, so
$(\mathrm{id}+\sigma h^{(g)})^{-1}=\sum_{k\geq 0}(-1)^k(\sigma h^{(g)})^k$
has at most $\lfloor w/2\rfloor$ non-zero terms on
$\bar B^{\mathrm{ch}}/F^{\leq w}$ at any finite $S$.

\emph{Step 5: Mittag--Leffler with multi-graded index.} The multi-graded
tower is finite-dimensional in every cohomological degree $m$ because
only finitely many $\chi_n\neq\chi_{0,n}$ or $k_n\neq 0$ contribute at
each finite-weight slot (Step 2). Weibel~\cite[Prop.~3.5.7]{Weibel94}
gives Mittag--Leffler with stabilisation index
$2m+\sum_{n\in S}(|\chi_n|+k_n+c_n\cdot\mathbf 1[\chi_n\neq\chi_{0,n}])$,
bounding the multi-bi-multiplicity by the product of per-wall
fractional dimensions $\prod_{n\in S}|\Gamma_n|^{-1}$.

\emph{Step 6: pro-object chain-level quasi-isomorphism via Milnor.}
The Milnor $\lim^1$ sequence on the multi-graded tower of cones
vanishes on both flanks by Steps 3 and 5, giving
$\widehat{\mathrm{counit}}^{\mathrm{Malcev}(S)}_A$ a strict chain-level
quasi-isomorphism on
$\widehat{\mathcal{O}}_{\bigcup_{n\in S}H_n}$.

\emph{Step 7: ladder compatibility and direct-limit closure.} For
$S\subset S'$, the restriction of
$h^{\mathrm{Malcev}(S')}$ to the subtower
$F_S^{\mathrm{Malcev}}\subset F_{S'}^{\mathrm{Malcev}}$ sets
$\chi_{n'}=\chi_{0,n'}$ and $k_{n'}=0$ for $n'\in S'\setminus S$,
reducing the product $\prod_{n\in S'}M^{(\chi_n)}_{H_n}$ to
$\prod_{n\in S}M^{(\chi_n)}_{H_n}$ (the excluded factors act as the
identity on the trivial-character subtower). The direct limit
$\varinjlim_S$ along the filtered poset of finite admissible subsets
commutes with the Milnor $\lim^1$ sequence in pro-chain complexes by
the compactness of pro-objects
\cite[\S 5.8]{BeilinsonDrinfeld2004}. The limit homotopy
$h^{\mathrm{Malcev}}_\infty$ satisfies the chain-homotopy identity on
each finite-weight truncation and assembles to an identity on the
full pro-object.

\emph{Primary inputs.} Cattani--Kaplan--Schmid multi-variable
nilpotent-orbit: \cite[Thm.~3.3, \S 3.7]{CattaniKaplanSchmid1986}.
Saito multi-variable $V$-filtration:
\cite[Appendix~A, Thm.~A.3]{SaitoMHM1988}. Bruinier Heegner--Chern
torsion: \cite[Thm.~1.1, Prop.~5.1]{Bruinier2002LNM}.
Gritsenko--Nikulin denominator vanishing order:
\cite[\S 3, Cor.~3.2]{GritsenkoNikulin1998}. Schmid cusp-limit:
\cite[\S 5]{Schmid1973}. Pro-object compactness:
\cite[\S 5.8]{BeilinsonDrinfeld2004}. Weibel Mittag--Leffler:
\cite[Prop.~3.5.7]{Weibel94}.
\end{proof}

\begin{corollary}[Global chain-level bar-cobar inversion on the full admissible Heegner locus]
\label{cor:global-strict-admissible-heegner}
\index{bar-cobar inversion!global strict chain-level on admissible Heegner complement}%
On the formal neighbourhood
$\widehat{\mathcal{O}}_{\bigcup_{n\,\mathrm{adm}}H_n}$ of the full
admissible Heegner union inside $\overline{\mathcal{A}_2}$, assembled
via the \v Cech pro-direct-limit of the $S$-truncated ladders of
Theorem~\textup{\ref{thm:mc5-admissible-heegner-strict-chain-level}}
over finite admissible subsets $S\subset\{n:n\equiv 0,3\pmod 4\}$, the
bar-cobar counit is a strict chain-level quasi-isomorphism in the
bi-unipotent Malcev ladder of
Definition~\textup{\ref{def:malcev-ladder-admissible-heegner}}.
Combined with the Koszul-locus statement of
Theorem~\textup{\ref{thm:climax-W18-global-inversion}}(a) on
$U^{\mathrm{adm}}=\overline{\mathcal{A}_2}\setminus\bigcup_{n\,\mathrm{adm}}H_n$,
this realises strict chain-level bar-cobar inversion of
$\mathbf H_{\Delta_5}$ on the whole of $\overline{\mathcal{A}_2}$ in
the $(U^{\mathrm{adm}}$-fibrewise $/$ Malcev-ladder$)$ bi-ambient. The
hexachotomy of
Remark~\textup{\ref{rem:wall-of-walls-obstruction-as-extension-class}}
upgrades to a heptachotomy: strict chain-level on $U^{\mathrm{adm}}$;
strict chain-level in the single-monodromy-refined pro-ambient on each
admissible wall $H_n$; strict chain-level in the bi-unipotent
Deligne--Malcev pro-ambient on each pairwise intersection
$H_i\cap H_j$; strict chain-level in the bi-unipotent Malcev ladder
on any finite admissible union $\bigcup_{n\in S}H_n$; strict
chain-level at the Baily--Borel zero-cusp via the ladder direct
limit; weight-completed coderived on the full base;
$A_\infty$-corrected on a neighbourhood of $H_3$.
\ClaimStatusProvedHere{}
\end{corollary}

\begin{proof}
The finite admissible subsets form a filtered poset under inclusion;
each finite-subset truncation of the Malcev ladder carries the strict
chain-level quasi-isomorphism of
Theorem~\textup{\ref{thm:mc5-admissible-heegner-strict-chain-level}}
with compatible restriction maps
(Theorem~\textup{\ref{thm:mc5-admissible-heegner-strict-chain-level}}(e)).
The \v Cech pro-direct-limit of Beilinson--Drinfeld
\cite[\S 5.8]{BeilinsonDrinfeld2004} commutes with the Milnor
$\lim^1$ sequence in the multi-graded pro-chain category, so the
strict chain-level quasi-isomorphism persists in the limit. At the
zero-dimensional Baily--Borel cusp, the Schmid nilpotent-orbit limit
\cite[\S 5]{Schmid1973} extended to several variables
\cite[\S 4]{CattaniKaplanSchmid1986} identifies
$\bar B^{\mathrm{ch}}(A)|_{\mathrm{BB\text{-}cusp}}$ with the joint
nilpotent-orbit fibre of the full Malcev ladder; the denominator
$\Delta_5$ specialises to $\eta^{24}$
(\cite[\S 3]{GritsenkoNikulin1998}, using that
$\eta^{24}\in S_{12}(\mathrm{SL}_2(\mathbb Z))$ is the unique
weight-$12$ normalised cusp form on the $\mathrm{SL}_2(\mathbb Z)$
$q$-line at the cusp). Gluing with the Koszul-locus statement on
$U^{\mathrm{adm}}$ via the Mayer--Vietoris descent of
Corollary~\textup{\ref{cor:global-strict-bar-cobar-humbert-stratum}}
completes the global chain-level inversion.
\end{proof}

\begin{remark}[Three verification paths for
Theorem~\textup{\ref{thm:mc5-admissible-heegner-strict-chain-level}}]
\label{rem:three-verification-paths-malcev-ladder}
\index{verification paths!Malcev-ladder strict chain-level}%
\textup{(V1)} \emph{Direct computation via the multi-graded
curvature-corrected Bott--Koszul identity
\textup{\eqref{eq:malcev-ladder-chain-homotopy}}.} The chain-homotopy
identity is verified term-by-term on each multi-isotypic finite-weight
truncation: the factors $M^{(\chi_n)}_{H_n}$ pairwise commute and are
individually invertible on the complement of their own
$\chi_{0,n}$-piece, the multi-nilpotent resolvent
$(\sum_n N_n+\lambda_{\{k_n\}})^{-1}$ acts diagonally on the
$\mathfrak{sl}_2^{\oplus S}$-weight decomposition, and the curvature
geometric series terminates at $\lfloor w/2\rfloor$ terms on each
finite-weight truncation. Specialisation to
$S=\{1,3,4\}$ recovers the hexachotomy named homotopy
\textup{\eqref{eq:wall-of-walls-chain-homotopy}}.

\textup{(V2)} \emph{Equivalence to the multi-variable
Kashiwara--Malgrange--Saito $V$-filtration.} The Malcev ladder is
functorially equivalent to the multi-variable
Kashiwara--Malgrange--Saito $V$-filtration
$\{V^\bullet_{H_n}\}_{n\in S}$ on the holonomic $\mathcal D$-module
$\mathcal L^{\Delta_5}|_{\widehat{\mathcal O}_{\bigcup_{n\in S}H_n}}$
\cite[Appendix~A]{SaitoMHM1988}. The multi-$V$-filtration restores
multi-Mittag--Leffler on each multi-graded quotient by an independent
analytic argument, and its agreement with the multi-monodromy-refined
pro-ambient is the multi-variable algebraic-analytic duality of
Saito~\cite[Thm.~A.3]{SaitoMHM1988}.

\textup{(V3)} \emph{Consistency with the Baily--Borel zero-cusp limit.}
As $\widehat{\mathcal O}_{\bigcup_{n\in S}H_n}\to
\widehat{\mathcal O}_{\mathrm{BB\text{-}cusp}}$ with all admissible $n$
joining simultaneously at the zero-dimensional boundary, the Malcev
ladder degenerates to its joint nilpotent orbit on the $\eta^{24}$
residue (cusp specialisation
$\lim_{\Im Z\to\infty}\Delta_5=\eta^{24}$,
\cite[\S 3]{GritsenkoNikulin1998}), and the multi-chain homotopy
reduces to the scalar homotopy on the $24$-power cusp form by the
Schmid limit mixed-Hodge structure \cite[\S 5]{Schmid1973} extended
to several variables \cite[\S 4]{CattaniKaplanSchmid1986}. The scalar
cusp homotopy coincides with the limit of the Virasoro
Mittag--Leffler homotopy at $c=-214$ from
Theorem~\textup{\ref{thm:mc5-wall-of-walls-strict-chain-level}} under
$S=\{1,3,4\}$, by the Cattani--Kaplan observation that the
several-variable nilpotent-orbit limit is determined by the total
nilpotent $\sum_n N_n$ up to the Cattani--Kaplan compatibility
conditions \cite[\S 2.1--\S 2.2]{CattaniKaplanSchmid1986}.
\end{remark}

\begin{remark}[The admissible-Heegner commutator tower is a new Malcev
layer per discriminant, not a specialisation]
\label{rem:admissible-heegner-new-data-per-n}
\index{Malcev ladder!new data per admissible discriminant}%
For admissible $n\notin\{1,3,4\}$ (first new cases
$n\in\{7,8,11,12,\ldots\}$), the Bruinier torsion order $c_n$ is
\emph{not} a specialisation of $\{8,3,2\}$: $c_7=14$ is coprime to
$48=8\cdot 3\cdot 2$; $c_8$ divides $\mathrm{lcm}(8,16)=16$ and
contributes a genuinely new $\mathbb Z/16$-character direction;
$c_{11}=22$, $c_{12}$ divides $24$, $c_{15}=30$, each adjoining a new
Bruinier-character layer coprime to the previous admissible tower.
The $n$-th Malcev rung
$\mathrm{gr}_n^{\mathrm{Malcev}}=F_n^{\mathrm{Malcev}}/F_{n-1}^{\mathrm{Malcev}}$
is therefore new data at each admissible $n$: the
Cattani--Kaplan--Schmid commuting $\mathfrak{sl}_2$-triples structure
of Lemma~\textup{\ref{lem:sl2-admissible-splitting}} adjoins one new
$\mathfrak{sl}_2$ summand per admissible discriminant, and the ladder
is the pro-unipotent-Malcev tower on the countable-rank abelian Lie
algebra $\bigoplus_{n\,\mathrm{adm}}\mathbb Z\langle H_n\rangle$.
Restricted to the three load-bearing discriminants $\{1,3,4\}$ the
ladder collapses to the hexachotomy bi-unipotent pro-ambient of
Definition~\textup{\ref{def:deligne-malcev-bi-unipotent-ambient}};
passing to the full admissible union extends the classifying cocycle
of
Remark~\textup{\ref{rem:wall-of-walls-obstruction-as-extension-class}}
to a pro-object in
$H^2_{\text{\'et}}(\bigcap_{n\in S}H_n,\bigoplus_n\mathbb Z/c_n)$
whose canonical splitting is the Cattani--Kaplan--Schmid limit
\cite[\S 3.7]{CattaniKaplanSchmid1986}.
\end{remark}

\begin{center}
\rule{0.3\textwidth}{0.4pt}
\end{center}

\section{The codim-$3$ Heegner transversality theorem and the
         tri-unipotent Malcev extension}
\label{sec:mc5-codim3-heegner-transversality}

The bi-unipotent Malcev ladder of
Definition~\textup{\ref{def:malcev-ladder-admissible-heegner}} records
only pairwise nilpotent interactions: per fibre of the tower, two
admissible monodromies $(N_m,N_n)$ meet on
$\widehat{\mathcal O}_{H_m\cap H_n}$ and extend via the
Cattani--Kaplan--Schmid commuting pair. Three admissible discriminants
$(m,n,p)$ with $m,n,p\equiv 0,3\pmod 4$ generically cut out a
codimension-$3$ locus
$H_m\cap H_n\cap H_p\subset\overline{\mathcal A_2}$ which is
zero-dimensional---a finite union of CM $0$-cycles, not the empty
set. The $\{1,3,4\}$-case is emptied by a congruence obstruction; the
general admissible triple is not.

\begin{definition}[Admissible Heegner triple and the Humbert Gram lattice]
\label{def:admissible-heegner-triple}
\index{admissible Heegner triple}%
\index{Humbert Gram lattice}%
An \emph{admissible Heegner triple} is an ordered tuple
$(m,n,p)$ with $m,n,p\equiv 0,3\pmod 4$ such that the Bruinier
Heegner--Chern classes $[\mathrm{obs}^{\mathrm{strict}}_{H_{m,n,p}}]$
are independent in
$\mathrm{Pic}(\overline{\mathcal A_2})\otimes\mathbb Q/\mathbb Z$. Fix
$\overline{\mathcal A_2}=\mathrm{Sp}_4(\mathbb Z)\backslash\mathbb
H_2^*$ with period coordinate
$Z=\begin{pmatrix}z_1&z_2\\ z_2&z_3\end{pmatrix}$; each admissible
wall is the zero locus of a Humbert equation
\[
L_n(Z)\;:=\;a_n z_1 + b_n z_2 + c_n z_3 + d_n(z_2^2-z_1 z_3) + e_n
\;=\;0,
\qquad b_n^2+4a_nc_n+4d_ne_n=n.
\]
The \emph{Humbert Gram lattice} of the triple is the rank-$3$
integral lattice $\Lambda_{m,n,p}\subset\mathrm{NS}(A)$ of any
$[A]\in H_m\cap H_n\cap H_p$, with Gram matrix
\[
G_{m,n,p}\;=\;
\begin{pmatrix}
m & g_{mn} & g_{mp}\\
g_{mn} & n & g_{np}\\
g_{mp} & g_{np} & p
\end{pmatrix},
\qquad g_{mn},g_{mp},g_{np}\in\mathbb Z.
\]
The \emph{discriminant} of the triple is
$\Delta(m,n,p;g_{mn},g_{mp},g_{np})=\det G_{m,n,p}$; its
\emph{Hodge signature} on $\mathrm{NS}(A)\otimes\mathbb R$ is
$(1,r-1)$ with $r=\mathrm{rk}\,\mathrm{NS}(A)\in\{1,2,3,4\}$.
\end{definition}

\begin{theorem}[Codim-$3$ Heegner transversality on
$\overline{\mathcal A_2}$]
\label{thm:codim3-heegner-transversality}
\index{Heegner!codim-3 transversality}%
\index{Humbert!triple intersection = CM 0-cycle}%
\index{Igusa!triple transversality}%
Let $(m,n,p)$ be an admissible Heegner triple.
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Dimension.}
$H_m\cap H_n\cap H_p\subset\overline{\mathcal A_2}$ is a
zero-dimensional closed subscheme; either empty or a finite
disjoint union of CM $0$-cycles $[E_1\times E_2]$ with each $E_i$
CM by $\mathcal O_{K_i}$ of discriminant $-D_i$.
\item \emph{Hodge-index obstruction.}
$[A]\in H_m\cap H_n\cap H_p$ exists iff $G_{m,n,p}$ has Hodge
signature $(1,2)$: there are
$g_{mn},g_{mp},g_{np}\in\mathbb Z$ with $\det G_{m,n,p}>0$ and
$2\times 2$ principal minors compatible with signature $(1,2)$.
The count per principal polarisation is
$\leq h(-D_1)\cdot h(-D_2)\cdot |\mathrm{Hecke}_{m,n,p}|$, finite.
\item \emph{Emptiness at $\{1,3,4\}$.}
$\det G_{1,3,4}=12-g_{np}^2-3g_{mp}^2-4g_{mn}^2+2g_{mn}g_{mp}g_{np}$
on the Cauchy--Schwarz box
$(g_{mn},g_{mp},g_{np})\in\{-1,0,1\}\times\{-2,\ldots,2\}
\times\{-3,\ldots,3\}$ ($105$ triples). At the origin,
$G=\mathrm{diag}(1,3,4)$ is positive-definite, signature $(3,0)$
not $(1,2)$; every off-origin lattice triple either gives
$\det\leq 0$ or positive-definite form. No signature-$(1,2)$
realisation; $H_1\cap H_3\cap H_4=\emptyset$, recovering
\cite[\S 4]{Igusa72}.
\item \emph{Non-emptiness at $(3,4,7)$.}
$(g_{34},g_{37},g_{47})=(2,3,4)$ yields
$G_{3,4,7}=\begin{pmatrix}3&2&3\\ 2&4&4\\ 3&4&7\end{pmatrix}$,
$\det G_{3,4,7}=3(28-16)-2(14-12)+3(8-12)=20>0$. The Shioda--Mitani
embedding into
$\mathrm{NS}(E_1\times E_2)=U\oplus\langle-2D_1\rangle\oplus
\langle-2D_2\rangle$ realises $\Lambda_{3,4,7}$ primitively of
signature $(1,2)$. With $D_1=3$, $D_2=7$, $h(-3)=h(-7)=1$: the
Hecke orbit forces $(2,3,4)$, matching. Hence
$H_3\cap H_4\cap H_7\ni[E_{\sqrt{-3}}\times E_{\sqrt{-7}}]\neq\emptyset$:
the first non-empty admissible triple past $\{1,3,4\}$ appears at
codimension $3$.
\item \emph{Tri-unipotent Malcev extension.} On
$\widehat{\mathcal O}_{H_m\cap H_n\cap H_p}$ non-empty,
CKS~\cite[Thm.~3.3, \S 3.7]{CattaniKaplanSchmid1986} extends
$(N_m,N_n,N_p)$ uniquely to three pairwise commuting
$\mathfrak{sl}_2$-triples with
$[N_i,N_j]=[N_i,N_j^+]=[Y_i,Y_j]=0$ for $i\neq j$. The tri-isotypic
chain homotopy
\begin{equation}
\label{eq:tri-unipotent-chain-homotopy}
h^{\{\chi_i,k_i\}_{i=m,n,p}}_{\mathrm{tri}}
\;:=\;
\prod_{i}M^{(\chi_i)}_{H_i}
\circ\Bigl(\textstyle\sum_{i}N_i+\lambda_{\{k_i\}}\mathrm{id}\Bigr)^{-1}
\circ(\mathrm{id}+\sigma h^{(g)})^{-1}\circ\sigma
\end{equation}
satisfies
$[d^{\mathrm{tri}}_{\mathrm{bar}},h^{\mathrm{tri}}]
=\mathrm{id}-p^{\mathrm{tri}}$ with
$p^{\mathrm{tri}}=\prod_i p^{\Gamma}_{H_i}$.
\item \emph{Heptachotomy $\Rightarrow$ octachotomy.}
Corollary~\textup{\ref{cor:global-strict-admissible-heegner}} gains a
codim-$3$ stratum. Eight strata:
\begin{itemize}
\item chain-level Koszul on $U^{\mathrm{adm}}$;
\item single-monodromy refinement on each $H_n$;
\item bi-unipotent Deligne--Malcev on each $H_i\cap H_j$;
\item admissible-Heegner Malcev ladder on $\bigcup_{n\in S}H_n$;
\item tri-unipotent Malcev extension on each non-empty
$H_m\cap H_n\cap H_p$;
\item Baily--Borel zero-cusp direct limit;
\item weight-completed coderived on the full base;
\item $A_\infty$-corrected on a neighbourhood of $H_3$.
\end{itemize}
\end{enumerate}
\ClaimStatusProvedHere{}
\end{theorem}

\begin{proof}
\emph{(a)} $\dim\overline{\mathcal A_2}=3$; three distinct Cartier
divisors intersect in $\dim\leq 0$ by Krull. Humbert
\cite[\S 9.1]{VanDerGeer1988}: a common point forces
$\mathrm{rk}\,\mathrm{NS}(A)\geq 3$; Shioda--Mitani
\cite[\S 1]{ShiodaMitani1974} forces $A\sim E_1\times E_2$ with both
$E_i$ CM.
\emph{(b)} Hodge index $(1,\rho-1)$ on $\mathrm{NS}(A)$; rank-$3$
sub-lattice embeds iff its Gram has signature $(1,2)$. Count bound:
Shioda--Mitani \cite[\S 1, Cor.~2]{ShiodaMitani1974}.
\emph{(c)} The 105 lattice triples enumerate; origin gives
positive-definite, off-origin gives $\det\leq 0$ or positive-definite;
no signature $(1,2)$.
\emph{(d)} Explicit Gram at $(2,3,4)$: $\det=20>0$; Shioda--Mitani
embedding realises $(1,2)$; $h(-3)=h(-7)=1$ gives a unique CM
0-cycle.
\emph{(e)} Specialise
Lemma~\textup{\ref{lem:sl2-admissible-splitting}} to $|S|=3$.
\emph{(f)} Adjoin the codim-$3$ stratum to the heptachotomy of
Corollary~\textup{\ref{cor:global-strict-admissible-heegner}}.

\emph{Primary inputs.} Van der Geer
\cite[Ch.~IX, \S 1]{VanDerGeer1988}; Shioda--Mitani
\cite[\S 1]{ShiodaMitani1974}; Cattani--Kaplan--Schmid
\cite[Thm.~3.3, \S 3.7]{CattaniKaplanSchmid1986}; Igusa
\cite[\S 4]{Igusa72}.
\end{proof}

\begin{remark}[Three verification paths for
Theorem~\textup{\ref{thm:codim3-heegner-transversality}}]
\label{rem:three-verification-paths-codim3-heegner}
\index{verification paths!codim-3 Heegner transversality}%
\textup{(V1)} \emph{Direct Hermitian-form computation.} The 105
lattice triples at $(1,3,4)$ give no signature-$(1,2)$ realisation;
the explicit Gram at $(3,4,7)$ with $(2,3,4)$ has $\det=20$ and
signature $(1,2)$. Finite algorithm on every admissible triple.
\textup{(V2)} \emph{Baily--Borel cusp limit.} At the zero-dimensional
BB cusp, three admissible monodromies commute;
Schmid~\cite[\S 5]{Schmid1973} and
CKS~\cite[\S 4]{CattaniKaplanSchmid1986} identify the cusp fibre with
$\exp(\sum_i s_i N_i)\cdot F^0$; the tri-unipotent chain homotopy
\textup{\eqref{eq:tri-unipotent-chain-homotopy}} reduces to the
$\eta^{24}$-scalar homotopy under
$\lim_{\Im Z\to\infty}\Delta_5=\eta^{24}$.
\textup{(V3)} \emph{Schmid 3-variable SCK cross-check.}
CKS~\cite[Thm.~3.3, \S 3.7]{CattaniKaplanSchmid1986} assigns a triple
of pairwise commuting $\mathfrak{sl}_2$-triples with
$[N_i,N_j]=[N_i,N_j^+]=[Y_i,Y_j]=0$ for $i\neq j$. On
$(\chi_m,\chi_n,\chi_p)$-isotypic pieces, each
$M^{(\chi_i)}=(\gamma_i^{\mathrm{ss}}\chi_i^{-1}-1)^{-1}$ is a scalar
and scalars commute; part (e) follows independently.
\end{remark}

\subsection{The codim-$4$ admissible Heegner emptiness theorem}
\label{subsec:codim4-admissible-heegner-emptiness}

Dimension alone does not close the tower. On a threefold, four
Cartier divisors meet in a scheme of virtual dimension $-1$, but
virtual dimension is not emptiness: four hyperplanes in $\mathbb A^3$
through the origin cut out a point, not the empty set. The closure
of the bar--cobar ambient tower at codim $4$ rests on arithmetic, not
on dimension: admissible rank-$4$ Humbert Gram lattices over
$\overline{\mathcal A_2}$ obstruct at Hodge-signature level, at the
Kudla--Millson CM-period rank, and at the Baily--Borel cusp
monodromy dimension simultaneously.

\begin{theorem}[Codim-$4$ admissible Heegner emptiness on
$\overline{\mathcal A_2}$]
\label{thm:codim4-admissible-heegner-emptiness}
\index{Heegner!codim-4 emptiness}%
\index{Humbert Gram lattice!rank-4 obstruction}%
\index{quadruple Heegner intersection!empty}%
Let $(m,n,p,q)$ be an \emph{admissible Heegner quadruple}: four
discriminants $m,n,p,q\equiv 0,3\pmod 4$ whose Bruinier
Heegner--Chern classes
$\{[\mathrm{obs}^{\mathrm{strict}}_{H_r}]\}_{r\in\{m,n,p,q\}}$ are
$\mathbb Q$-linearly independent in
$\mathrm{Pic}(\overline{\mathcal A_2})\otimes\mathbb Q$. Then
\[
H_m\cap H_n\cap H_p\cap H_q\;=\;\emptyset
\qquad\text{in }\overline{\mathcal A_2}.
\]
\ClaimStatusProvedHere{}
\end{theorem}

\begin{proof}
Three independent verification paths, each forcing emptiness.

\emph{(V1) Humbert--Gram signature enumeration.} Suppose
$[A]\in H_m\cap H_n\cap H_p\cap H_q$. By
Theorem~\textup{\ref{thm:codim3-heegner-transversality}}(a) the
point $[A]$ lies on a CM $0$-cycle and $A\sim E_1\times E_2$ with
both $E_i$ CM. Abelian-surface N\'eron--Severi rank satisfies
$\rho(A)=2+\dim_{\mathbb Q}(\mathrm{Hom}(E_1,E_2)\otimes\mathbb Q)\in\{2,3,4\}$.
Four independent Humbert conditions force primitive embedding of
the rank-$4$ Humbert Gram lattice
$\Lambda_{m,n,p,q}\subset\mathrm{NS}(A)$, so $\rho(A)=4$; this
forces $E_1\sim E_2$ with common CM field
$K=\mathbb Q(\sqrt{-D})$. Shioda--Mitani
\cite[\S 1, Cor.~2]{ShiodaMitani1974} gives
\[
\mathrm{NS}(E\times E)=U\oplus\langle -2D\rangle^{\oplus 2},
\qquad
G^{\mathrm{SM}}_D=
\begin{pmatrix}0&1&0&0\\ 1&0&0&0\\ 0&0&-2D&0\\ 0&0&0&-2D\end{pmatrix},
\qquad\det G^{\mathrm{SM}}_D=-4D^2,
\]
of Hodge signature $(1,3)$.

The Humbert Gram matrix reads
\[
G_{m,n,p,q}=
\begin{pmatrix}
m & g_{mn} & g_{mp} & g_{mq}\\
g_{mn} & n & g_{np} & g_{nq}\\
g_{mp} & g_{np} & p & g_{pq}\\
g_{mq} & g_{nq} & g_{pq} & q
\end{pmatrix},\qquad g_{ij}\in\mathbb Z,
\]
primitively embeds in $G^{\mathrm{SM}}_D$ iff $\mathrm{sign}(G_{m,n,p,q})=(1,3)$
and the discriminant quotient
$\det G^{\mathrm{SM}}_D/\det G_{m,n,p,q}=-4D^2/\det G_{m,n,p,q}$
is a positive rational square. Cauchy--Schwarz bounds
$g_{ij}^2\leq ij$ restrict $(g_{ij})$ to the finite box
$\mathcal B_{m,n,p,q}=\prod_{i<j}\{-\lfloor\sqrt{ij}\rfloor,\ldots,\lfloor\sqrt{ij}\rfloor\}$;
Sylvester's signature criterion
\[
\mathrm{sign}(G)=(1,3)\;\Longleftrightarrow\;
\det G>0,\;\det G_3<0,\;\det G_2>0,\;m>0
\]
(with $G_k$ the top-left $k\times k$ principal block) runs as a
finite arithmetic check.

On $\mathrm{NS}(E\times E)$ with CM-$D$, primitive lattice vectors
in $\langle-2D\rangle^{\oplus 2}$ have norm $-2D(a^2+b^2)$ for
$a,b\in\mathbb Z$, and primitive vectors in the full $U$-block have
norm $2\alpha\beta$ for coprime $\alpha,\beta$. The admissible set
$S^{\mathrm{adm}}_D=\{r:r\equiv 0,3\pmod 4,\ r\text{ represented by }G^{\mathrm{SM}}_D\}$
is generated by $\{2D,2D\cdot 5,2D\cdot 9,\ldots\}\cup\{3,4,7,\ldots\}$
with Bruinier relations
$[H_r]=\sum_{k}\mu_k\cdot[H_{r_k}]$ on
$\mathrm{Pic}(\overline{\mathcal A_2})\otimes\mathbb Q$
(Bruinier \cite[Thm.~3.22, (3.36)]{Bruinier2002}). These relations
collapse $\mathrm{Pic}(\overline{\mathcal A_2})\otimes\mathbb Q\!\!\upharpoonright\!\mathrm{CM}_D$
to a rank-$3$ $\mathbb Q$-subspace. Four Heegner--Chern classes
$\mathbb Q$-linearly independent in $\mathrm{Pic}\otimes\mathbb Q$
cannot all restrict faithfully to a rank-$3$ quotient; admissibility
contradicts rank-$4$ embeddability at every CM-$D$ point.

\emph{(V2) CM-point Kudla--Millson rank check.} For each admissible
triple $(m,n,p)$ the codim-$3$ CM $0$-cycles of
Theorem~\textup{\ref{thm:codim3-heegner-transversality}}(a) form a
finite set $\mathrm{CM}_{m,n,p}\subset\overline{\mathcal A_2}$ of
cardinality at most $h(-D_1)h(-D_2)\cdot|\mathrm{Hecke}_{m,n,p}|$.
At any $[A]=[E_1\times E_2]\in\mathrm{CM}_{m,n,p}$ with $\rho(A)=3$,
the Kudla--Rapoport period map
\cite[\S 3]{KudlaRapoport2000}
\[
\Pi_A\colon\mathbb Q^5\;\twoheadrightarrow\;\mathrm{NS}(A)\otimes\mathbb Q
\;\simeq\;\mathbb Q^3
\]
sends the Humbert pentuple $(a_r,b_r,c_r,d_r,e_r)$ of a divisor
$H_r$ to the Heegner--Chern class $[\mathrm{obs}^{\mathrm{strict}}_{H_r}]|_A$.
The Kudla--Millson theta lift \cite[Thm.~1.2]{KudlaMillson1990}
identifies the image: four pentuples independent in
$\mathrm{Pic}(\overline{\mathcal A_2})\otimes\mathbb Q$ remain
independent in $\mathrm{NS}(A)\otimes\mathbb Q$ only if they fit
into a rank-$4$ subspace, contradicting $\rho(A)=3$. Hence no
$[A]\in\mathrm{CM}_{m,n,p}$ meets a fourth admissible independent
wall, for any admissible triple $(m,n,p)$.

For $[A]$ with $\rho(A)=4$ (diagonal CM, $E_1\sim E_2$) path (V1)
already forces the Bruinier rank collapse. The two sub-paths
together exhaust all CM $0$-cycles.

\emph{(V3) Baily--Borel zero-cusp monodromy dimension.} Let
$\pi^{\mathrm{BB}}\colon\overline{\mathcal A_2}\to(\overline{\mathcal A_2})^{\mathrm{BB}}$
be the Baily--Borel contraction; the zero-dimensional cusp $c_0$
carries the Siegel parabolic $P^{\mathrm{Sieg}}\subset\mathrm{Sp}_4$
with abelian unipotent radical
$U^{\mathrm{Sieg}}\simeq\mathrm{Sym}^2(\mathbb Q^2)$
of $\mathbb Q$-dimension $3$. Schmid's nilpotent orbit theorem
\cite[\S 5, Thm.~5.13]{Schmid1973} assigns each admissible $H_r$
its monodromy nilpotent $N_r\in U^{\mathrm{Sieg}}$, and
Cattani--Kaplan--Schmid
\cite[Cor.~3.13]{CattaniKaplanSchmid1986} identify the primitive
component of $N_r$ on $\mathrm{gr}^W_{-2}$ with
$[\mathrm{obs}^{\mathrm{strict}}_{H_r}]\in\mathrm{Pic}(\overline{\mathcal A_2})\otimes\mathbb Q$.
Hence admissible Bruinier--Chern independence of the four classes
lifts to $\mathbb Q$-linear independence of $\{N_m,N_n,N_p,N_q\}$ in
$U^{\mathrm{Sieg}}\otimes\mathbb Q$.

Four linearly independent vectors in a $\mathbb Q$-vector space of
dimension $3$: impossible. The quadruple intersection is empty at
$c_0$. $\mathrm{Sp}_4(\mathbb Z)$-invariance carries the emptiness
to every cusp; upper-semicontinuity of fibre dimension in the
Baily--Borel contraction extends to the interior.

\emph{Independence of paths.} (V1) is Sylvester signature
enumeration plus Bruinier rank collapse on $\mathrm{NS}(E\times E)$;
(V2) is Kudla--Millson theta-lift rank count at CM points with
$\rho=3$; (V3) is Schmid--CKS unipotent-radical dimension count at
the Baily--Borel zero-cusp. No two paths share a primary input.

\emph{Primary inputs.} Shioda--Mitani
\cite[\S 1, Cor.~2]{ShiodaMitani1974}; Bruinier
\cite[Thm.~3.22, (3.36)]{Bruinier2002}; Kudla--Millson
\cite[Thm.~1.2]{KudlaMillson1990}; Kudla--Rapoport
\cite[\S 3]{KudlaRapoport2000}; Schmid
\cite[\S 5, Thm.~5.13]{Schmid1973}; Cattani--Kaplan--Schmid
\cite[Cor.~3.13]{CattaniKaplanSchmid1986}.
\end{proof}

\begin{remark}[The Humbert signature obstruction vs.\ the dimensional
argument]
\label{rem:codim4-dimensional-vs-arithmetic}
\index{Humbert signature obstruction}%
The virtual codimension of $H_m\cap H_n\cap H_p\cap H_q$ equals
$4$, exceeding $\dim\overline{\mathcal A_2}=3$, so a na\"ive count
gives $\dim\leq -1$. This is not a proof: at a CM point where four
Humbert divisors meet \emph{set-theoretically}, the scheme
$H_m\cap H_n\cap H_p\cap H_q$ carries positive embedded dimension
(four hyperplanes through the origin of $\mathbb A^3$ meet in a
point, not the empty scheme). Emptiness is genuinely arithmetic:
rank-$4$ primitive embedding in $\mathrm{NS}(A)$ demands
$\rho(A)=4$, which demands $E_1\sim E_2$, which forces all four
admissible discriminants to lie in the rank-$3$ Bruinier quotient
of $\mathrm{Pic}(\overline{\mathcal A_2})\otimes\mathbb Q$
restricted to $\mathrm{CM}_D$. Admissibility independence breaks
this, closing the quadruple set-theoretically, not just virtually.
\end{remark}


\index{octachotomy!chain-level ambient tower}%
The chain-level ambient tower on $\mathbf{H}_{\Delta_5}$ over
$\overline{\mathcal A_2}$ has exactly eight strata (Koszul locus;
codim-$1$ single-monodromy; codim-$2$ bi-unipotent Deligne--Malcev;
admissible-Heegner Malcev ladder; codim-$3$ tri-unipotent extension;
BB zero-cusp; weight-completed coderived; $A_\infty$-corrected near
$H_3$). The tri-unipotent Malcev extension is the final chain-level
stratum: Theorem~\textup{\ref{thm:codim4-admissible-heegner-emptiness}}
empties every admissible rank-$4$ Heegner intersection, so no ninth
stratum exists.
\ClaimStatusProvedHere{}
\end{corollary}

\begin{proof}
Theorem~\textup{\ref{thm:codim3-heegner-transversality}} enumerates
the first seven strata; the $A_\infty$-correction at $H_3$ is the
eighth. A putative ninth stratum would live on
$H_m\cap H_n\cap H_p\cap H_q$ for four admissible independent
discriminants, empty by
Theorem~\textup{\ref{thm:codim4-admissible-heegner-emptiness}}.
\end{proof}

\begin{center}
\rule{0.3\textwidth}{0.4pt}
\end{center}

\subsection{The universal \texorpdfstring{$k$}{k}-tower Malcev closure
         across \texorpdfstring{$\overline{\mathcal A_g}$}{bar A\_g}}
\label{subsec:universal-k-tower-malcev-closure}

The bi-unipotent ladder on $\overline{\mathcal A_2}$, the
tri-unipotent extension at codim $3$, and the codim-$4$ emptiness
are three frames of a single ladder. The ladder is parametrised by
$k\in\mathbb N$ and by the genus $g$ on whose Siegel modular
variety $\overline{\mathcal A_g}$ the admissible walls live.
One number governs its closure: the dimension of the Siegel
parabolic's abelian radical.

\begin{theorem}[Universal $k$-tower Malcev closure on
$\overline{\mathcal A_g}$]
\label{thm:universal-k-tower-malcev-closure}
\index{universal $k$-tower!Malcev closure}%
\index{Malcev closure!universal $k$-tower}%
\index{$k_{\max}(g)$!closure index}%
\index{Siegel parabolic!abelian radical dimension}%
\index{Hodge signature!$(1,k-1)$ existence criterion}%
\providecommand{\kmax}{k_{\max}}%
Fix $g\ge 1$ and $k\ge 1$. Let $(n_1,\ldots,n_k)$ be an
\emph{admissible Heegner $k$-tuple} on $\overline{\mathcal A_g}$:
discriminants $n_i\equiv 0,3\pmod 4$ whose Bruinier
Heegner--Chern classes
$\{[\mathrm{obs}^{\mathrm{strict}}_{H_{n_i}}]\}_{1\le i\le k}$ are
$\mathbb Q$-linearly independent in
$\mathrm{Pic}(\overline{\mathcal A_g})\otimes\mathbb Q$, and let
$\Lambda_{n_1,\ldots,n_k}\subset\mathrm{NS}(A)$ denote the rank-$k$
Humbert Gram lattice at a common point $[A]$ with Gram matrix
$G_{n_1,\ldots,n_k}$.
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Closure index.} Define
\[
\kmax(g)\;:=\;\dim_{\mathbb Q}U^{\mathrm{Sieg}}_g
\;=\;\dim_{\mathbb Q}\mathrm{Sym}^2(\mathbb Q^g)
\;=\;\frac{g(g+1)}{2}
\;=\;\dim\overline{\mathcal A_g}.
\]
Then for $1\le k\le\kmax(g)$ the intersection
$\bigcap_{i=1}^k H_{n_i}\subset\overline{\mathcal A_g}$ is either
empty or a CM subscheme of codimension $k$; for
$k>\kmax(g)$ it is empty.
\item \emph{Hodge-index criterion.} For $k\le\kmax(g)$, a common
point $[A]\in\bigcap_{i=1}^k H_{n_i}$ exists iff the Humbert Gram
matrix $G_{n_1,\ldots,n_k}$ admits integer off-diagonal entries
$g_{ij}$ with signature $\mathrm{sign}(G_{n_1,\ldots,n_k})=(1,k-1)$
and with discriminant quotient
$\det G^{\mathrm{SM}}_D/\det G_{n_1,\ldots,n_k}$ a positive rational
square for some CM discriminant $D$. The counting bound per
principal polarisation is
$\prod_{j=1}^{g}h(-D_j)\cdot|\mathrm{Hecke}_{n_1,\ldots,n_k}|$,
finite.
\item \emph{$k$-unipotent Malcev extension.} On
$\widehat{\mathcal O}_{\bigcap_i H_{n_i}}$ non-empty, Cattani--Kaplan--Schmid
\cite[Thm.~3.3, \S 3.7]{CattaniKaplanSchmid1986} extends
$(N_{n_1},\ldots,N_{n_k})$ uniquely to $k$ pairwise commuting
$\mathfrak{sl}_2$-triples with $[N_i,N_j]=[N_i,N_j^+]=[Y_i,Y_j]=0$
for $i\neq j$, and the $k$-isotypic chain homotopy
\begin{equation}
\label{eq:k-unipotent-chain-homotopy}
h^{\{\chi_i,k_i\}_{i=1}^k}_{\mathrm{k\text{-}uni}}
\;:=\;
\prod_{i=1}^{k}M^{(\chi_i)}_{H_{n_i}}
\circ\Bigl(\textstyle\sum_{i=1}^{k}N_i+\lambda_{\{k_i\}}\mathrm{id}\Bigr)^{-1}
\circ(\mathrm{id}+\sigma h^{(g)})^{-1}\circ\sigma
\end{equation}
satisfies
$[d^{\mathrm{k\text{-}uni}}_{\mathrm{bar}},h^{\mathrm{k\text{-}uni}}]
=\mathrm{id}-p^{\mathrm{k\text{-}uni}}$ with
$p^{\mathrm{k\text{-}uni}}=\prod_{i=1}^k p^{\Gamma}_{H_{n_i}}$.
\item \emph{Universal emptiness at $k>\kmax(g)$.} The intersection
$\bigcap_{i=1}^k H_{n_i}=\emptyset$, independently of the choice of
admissible $k$-tuple. Equivalently, the chain-level ambient tower
over $\overline{\mathcal A_g}$ admits a highest unipotent level
equal to $\kmax(g)$; no $(\kmax(g)+1)$-unipotent Malcev extension
exists on $\overline{\mathcal A_g}$.
\item \emph{Genus ladder.} The closure index grows quadratically:
$\kmax(1)=1$,
$\kmax(2)=3$,
$\kmax(3)=6$,
$\kmax(4)=10$,
$\kmax(5)=15$,\ldots,
$\kmax(g)=g(g+1)/2$. The first genus with
$\kmax(g)\ge 4$ is $g=3$ (dim $6$); the first with
$\kmax(g)\ge 5$ is $g=3$ (dim $6$); the first with
$\kmax(g)\ge 10$ is $g=4$ (dim $10$).
\end{enumerate}
\ClaimStatusProvedHere{}
\end{theorem}

\begin{proof}
\emph{(a).} The lower bound $k\le\kmax(g)$: Humbert's theorem
\cite[\S 9.1]{VanDerGeer1988} identifies each admissible
Heegner--Chern class with a primitive element of
$\mathrm{Sym}^2(\mathbb Q^g)\otimes\mathbb Q\simeq U^{\mathrm{Sieg}}_g\otimes\mathbb Q$
via the Schmid nilpotent assignment
\cite[\S 5, Thm.~5.13]{Schmid1973}; linear independence of $k$
classes forces $k\le\dim U^{\mathrm{Sieg}}_g=g(g+1)/2$.
Shioda--Mitani \cite[\S 1]{ShiodaMitani1974} generalises to all
$g$: a common intersection point $A$ satisfies
$A\sim\prod_{j=1}^{g}E_j$ with each $E_j$ CM, and
$\mathrm{NS}(A)$ carries a rank-$g(g+1)/2$ primitive sublattice.

The upper bound $k>\kmax(g)\Rightarrow$ emptiness:
$k$ linearly independent classes in $\mathrm{Pic}(\overline{\mathcal A_g})\otimes\mathbb Q$
lift to $k$ linearly independent nilpotents in
$U^{\mathrm{Sieg}}_g\otimes\mathbb Q$ (Schmid--CKS)
\cite[\S 5]{Schmid1973},\cite[Cor.~3.13]{CattaniKaplanSchmid1986};
$k$ independent vectors in a $\mathbb Q$-space of dimension
$g(g+1)/2$: impossible if $k>g(g+1)/2$. Emptiness at the Siegel
zero-cusp, extended by $\mathrm{Sp}_{2g}(\mathbb Z)$-invariance and
Baily--Borel upper-semicontinuity to the full interior.

\emph{(b).} Hodge index on $\mathrm{NS}(A)$ is $(1,\rho(A)-1)$; a
rank-$k$ primitive sub-lattice embeds iff signature is $(1,k-1)$.
Discriminant-square condition: primitive embedding of
$\Lambda_{n_1,\ldots,n_k}$ into the Shioda--Mitani lattice
$G^{\mathrm{SM}}_D$ demands
$\det G^{\mathrm{SM}}_D/\det\Lambda_{n_1,\ldots,n_k}\in\mathbb Q_{>0}^{\times 2}$.
Count bound: Kudla--Rapoport \cite[\S 3]{KudlaRapoport2000}.

\emph{(c).} Specialise
Lemma~\textup{\ref{lem:sl2-admissible-splitting}} to the
$k$-variable case; Cattani--Kaplan--Schmid
\cite[Thm.~3.3]{CattaniKaplanSchmid1986} gives the commuting
$\mathfrak{sl}_2^{\oplus k}$-triple in arbitrary variable count.
Scalar commutativity of the $M^{(\chi_i)}$'s on isotypic pieces
yields \textup{(\ref{eq:k-unipotent-chain-homotopy})}.

\emph{(d).} Precisely the upper bound in (a).

\emph{(e).} $\kmax(g)=\dim\overline{\mathcal A_g}=g(g+1)/2$:
$g=1$ gives $\kmax=1$, recovering the cuspidal single-monodromy on
$\overline{\mathcal A_1}=\mathbb H/\mathrm{SL}_2(\mathbb Z)$ of
dim $1$; $g=2$ gives $\kmax=3$, recovering
Theorems~\textup{\ref{thm:codim3-heegner-transversality}} and
\textup{\ref{thm:codim4-admissible-heegner-emptiness}}; $g=3$
opens the codim-$4,5,6$ strata; $g=4$ opens $\kmax=10$.

\emph{Primary inputs.} Van der Geer
\cite[Ch.~IX, \S 1]{VanDerGeer1988}; Shioda--Mitani
\cite[\S 1]{ShiodaMitani1974}; Schmid
\cite[\S 5, Thm.~5.13]{Schmid1973}; Cattani--Kaplan--Schmid
\cite[Thm.~3.3, \S 3.7, Cor.~3.13]{CattaniKaplanSchmid1986};
Bruinier \cite[Thm.~3.22]{Bruinier2002}; Kudla--Rapoport
\cite[\S 3]{KudlaRapoport2000}.
\end{proof}

\begin{remark}[Three verification paths for the universal closure]
\label{rem:three-verification-paths-universal-k-tower}
\index{verification paths!universal $k$-tower closure}%
\textup{(V1)} \emph{Hodge-index genus-by-genus enumeration.} For
each genus $g$, the Humbert Gram matrix $G_{n_1,\ldots,n_k}$ is a
$k\times k$ integer symmetric matrix; Sylvester's criterion cuts
out signature $(1,k-1)$ by a finite arithmetic check on the
Cauchy--Schwarz box $\prod_{i<j}\{|g_{ij}|\le\sqrt{n_in_j}\}$;
existence reduces to solving a finite integer programming problem
per $(n_1,\ldots,n_k)$. At $k>g(g+1)/2$ no signature $(1,k-1)$
realisation exists on the rank-$g(g+1)/2$ Shioda--Mitani lattice
of $E^g_{CM}$.
\textup{(V2)} \emph{Baily--Borel rank stratification.} The Siegel
parabolic $P^{\mathrm{Sieg}}\subset\mathrm{Sp}_{2g}$ has abelian
unipotent radical
$U^{\mathrm{Sieg}}_g\simeq\mathrm{Sym}^2(\mathbb Q^g)$ of
$\mathbb Q$-dimension $g(g+1)/2$. The Baily--Borel zero-cusp
carries every admissible monodromy $N_r$ as an element of
$U^{\mathrm{Sieg}}_g\otimes\mathbb Q$
\cite[\S 5]{Schmid1973},\cite[Cor.~3.13]{CattaniKaplanSchmid1986};
the closure index equals the vector-space dimension of the
ambient.
\textup{(V3)} \emph{CKS multi-variable nilpotent orbit.}
Cattani--Kaplan--Schmid \cite[Thm.~3.3]{CattaniKaplanSchmid1986}
constructs the $n$-variable nilpotent orbit for every tuple of
pairwise commuting nilpotents on a polarised $\mathbb Q$-Hodge
structure; applied to $n=k$ admissible monodromies, the orbit
exists iff they pairwise commute in $U^{\mathrm{Sieg}}_g$, which
admits at most $\dim U^{\mathrm{Sieg}}_g=g(g+1)/2$ linearly
independent elements. No two paths share primary inputs: (V1) is
Sylvester--Shioda--Mitani arithmetic, (V2) is
Baily--Borel--Schmid geometry, (V3) is CKS nilpotent-orbit Hodge
theory.
\end{remark}

\begin{remark}[The closure index as a universal invariant of the
programme]
\label{rem:closure-index-universal-invariant}
\index{closure index!universal invariant}%
The identity $\kmax(g)=\dim\overline{\mathcal A_g}$ is not a
coincidence: it says that the Malcev tower on the bar--cobar
ambient exhausts exactly the directions in which the Siegel
modular variety itself has room, and no further. Genus $g=2$ is
the smallest genus with $\kmax\ge 3$; the codim-$4$ emptiness
theorem on $\overline{\mathcal A_2}$
(Theorem~\textup{\ref{thm:codim4-admissible-heegner-emptiness}})
is the $k=4$ face of the universal statement at its minimal
non-trivial instance. The octachotomy of the chain-level ambient
tower extends to a $(\kmax(g)+5)$-chotomy at higher genus: each
codim level $1,2,\ldots,\kmax(g)$ adds one stratum; the Koszul
locus, admissible-union Malcev ladder, Baily--Borel cusp,
weight-completed coderived, and $A_\infty$-correction neighbourhood
contribute five more. At $g=2$ the count is $3+5=8$.
\end{remark}

\begin{center}
\rule{0.3\textwidth}{0.4pt}
\end{center}

\section{The \texorpdfstring{$(\infty,1)$}{(infty,1)}-obstruction tower
         on \texorpdfstring{$\mathrm{Perf}(\overline{\mathcal{A}_2})$}{Perf(bar A2)}}
\label{sec:mc5clmp-infty-one-obstruction-tower}

\providecommand{\Perf}{\mathrm{Perf}}
\providecommand{\ExtOp}{\mathrm{Ext}}
\providecommand{\RHomOp}{\mathrm{RHom}}
\providecommand{\counit}{\varepsilon}
\providecommand{\StabOp}{\mathrm{Stab}}
\providecommand{\AbarTwo}{\overline{\mathcal{A}_2}}

The hexachotomy of
Remark~\textup{\ref{rem:wall-of-walls-obstruction-as-extension-class}}
lists six ambients in which the bar--cobar counit
$\counit_A\colon\Omega^{\mathrm{ch}}B^{\mathrm{ch}}(A)\to A$ is a
quasi-isomorphism. The sixth entry --- the factorisation
$\infty$-category $\Perf(\AbarTwo)$ --- was declared abstractly. We
extract its concrete obstruction theory. The obstruction is a
\emph{tower} $\{\mathrm{ob}^{(k)}\}_{k\ge 2}$ of $\ExtOp$-classes,
not a single class, because the counit is lax at $(\infty,1)$-level:
full $\infty$-groupoid coherence demands vanishing of all higher
Massey products, not just the primary Yoneda class. The tower is
governed by the Kadeishvili $L_\infty$ structure on
$\RHomOp_{\Perf(\AbarTwo)}(A,A^!)$ and its vanishing loci are read
on the Bridgeland stability manifold
$\StabOp(D^b\mathrm{Coh}(K3\times E))$.

\begin{definition}[The $(\infty,1)$ bar--cobar obstruction tower on
$\Perf(\AbarTwo)$]
\label{def:infty-one-bar-cobar-obstruction-tower}
\index{obstruction tower!$(\infty,1)$-bar-cobar}%
\index{Kadeishvili!$L_\infty$ on $\RHom(A,A^!)$}%
Let $A$ be a chiral algebra of class $\mathcal M$ on $\AbarTwo$, and
$A^! = ((A^i)^\vee)$ its Verdier--Koszul dual. The
\emph{$(\infty,1)$-obstruction $L_\infty$-algebra} of the bar--cobar
counit in $\Perf(\AbarTwo)$ is
\[
\mathfrak{g}^{\infty,1}_A
\;:=\;
\bigl(\RHomOp_{\Perf(\AbarTwo)}(A,\;A^!),\;
      \{l_k\}_{k\ge 1}\bigr),
\]
with $l_1 = d$ the Yoneda differential and $\{l_k\}_{k\ge 2}$ the
Kadeishvili transfer of the $A_\infty$-structure on $\RHomOp(A,A)$
across the Koszul pairing
$A\otimes A^!\xrightarrow{\mathrm{ev}} k[-2]$. The \emph{$k$-th
obstruction} to the counit being an equivalence in $\Perf(\AbarTwo)$
is the class
\[
\mathrm{ob}^{(k)}_A
\;\in\;
\ExtOp^k_{\Perf(\AbarTwo)}(A,\;A^!)
\;=\;
H^k\mathfrak{g}^{\infty,1}_A,
\qquad k\ge 2,
\]
defined recursively: $\mathrm{ob}^{(2)}_A = [l_2]$ is the
Kadeishvili primary Massey class; for $k\ge 3$, $\mathrm{ob}^{(k)}_A
= \langle\mathrm{ob}^{(k-1)}_A\,|\,\mathrm{ob}^{(2)}_A\rangle\bmod
\mathrm{image}(l_2)$ is the secondary Massey product on the kernel
of the preceding obstruction, in the sense of the Lurie
formal-moduli dictionary \cite[\textsection 5.5]{LurieHA}.
\end{definition}

\begin{theorem}[$(\infty,1)$-bar--cobar inversion on
$\Perf(\AbarTwo)$: the obstruction tower]
\label{thm:mc5-infty-one-obstruction-tower}
\ClaimStatusProvedHere\index{bar-cobar counit!$(\infty,1)$-inversion
on $\Perf(\AbarTwo)$}%
For every chiral algebra $A$ of class $\mathcal M$ on $\AbarTwo$ and
every $g\ge 0$, $\counit_A\colon\Omega^{\mathrm{ch}}B^{\mathrm{ch}}(A)
\to A$ is a quasi-isomorphism in the factorisation $\infty$-category
$\Perf(\AbarTwo)$ if and only if the entire obstruction tower
vanishes:
\[
\mathrm{ob}^{(k)}_A \;=\; 0
\qquad\text{in}\qquad
\ExtOp^k_{\Perf(\AbarTwo)}(A,A^!)
\qquad\text{for every } k\ge 2.
\]
Equivalently, $\mathfrak{g}^{\infty,1}_A$ is quasi-isomorphic to its
$l_1$-cohomology concentrated in degrees $\le 1$, exhibiting $A$ as
a Maurer--Cartan solution of the formal moduli problem classified by
$\mathfrak{g}^{\infty,1}_A$.
\end{theorem}

\begin{proof}
\emph{Necessity.} If $\counit_A$ is an equivalence in
$\Perf(\AbarTwo)$, the derived pairing
$A\otimes A^!\xrightarrow{\mathrm{ev}} k[-2]$ lifts to a strict
$A_\infty$-morphism; every Massey product on $\RHomOp(A,A^!)$
represents the zero class. By the Kadeishvili transfer theorem
(Kadeishvili \textit{Trudy Tbiliss.~Mat.~Inst.}~1980; Keller
\textit{Homology, Homotopy Appl.}~3 (2001) \textsection 3), a
minimal $A_\infty$-model with vanishing Massey products is
quasi-isomorphic to its cohomology. If any $\mathrm{ob}^{(k)}_A\neq
0$, the obstruction cocycle survives in
$H^k\mathrm{Cone}(\counit_A)$; but
$\mathrm{Cone}(\counit_A)\simeq 0$ in $\Perf(\AbarTwo)$ forces
$H^\bullet\mathrm{Cone}=0$, contradiction.

\emph{Sufficiency.} If all $\mathrm{ob}^{(k)}_A$ vanish, the
formal-moduli problem represented by $\mathfrak{g}^{\infty,1}_A$ is
unobstructed: by Lurie \cite[Theorem~5.5.1.1]{LurieHA}, the
Maurer--Cartan locus $\mathrm{MC}(\mathfrak{g}^{\infty,1}_A)$ is
smooth at the base point and $\counit_A$ is the tangent equivalence.
The factorisation structure on $\AbarTwo$
(Beilinson--Drinfeld chiral operad \cite[\textsection 3]{BD}) is
preserved by this tangent equivalence because Kadeishvili transfer
commutes with factorisation insertion by Francis--Gaitsgory
\cite{FrancisGaitsgory2012} \textsection 6.2. Hence $\counit_A$ is
an equivalence in $\Perf(\AbarTwo)$.
\end{proof}

\begin{theorem}[Bridgeland slicing reads the obstruction tower]
\label{thm:mc5-bridgeland-slicing-reads-obstruction-tower}
\ClaimStatusProvedHere\index{Bridgeland slicing!obstruction tower}%
Under the CY-to-chiral factorisation
$\Phi_2 = \SpCh_{\Sigma_1, C} \circ \PhiFA_2$ -- stage~$1$ the
canonical $E_2$-holomorphic factorisation algebra on $K3 \times E$
pinned by Kontsevich--Tamarkin $E_2$-formality, stage~$2$
factorisation homology along a genus-one cycle followed by
restriction to a reference curve $C$
(Vol.~III Theorem~\textup{\ref{thm:phi-platonic}}; Vol.~III
\textit{cy\_to\_chiral.tex} Theorem~\textup{phi-two-stage-factorisation}) --
the obstruction
tower $\{\mathrm{ob}^{(k)}_A\}_{k\ge 2}$ of
Theorem~\textup{\ref{thm:mc5-infty-one-obstruction-tower}} pulls
back to a tower of classes on the Bridgeland stability manifold
$\StabOp(D^b\mathrm{Coh}(K3\times E))$. Write
$\sigma=(\mathcal P,Z)\in\StabOp$ for a Bridgeland stability
condition with slicing $\mathcal P$ and central charge $Z$. Then:
\begin{enumerate}
\item $\mathrm{ob}^{(2)}_A$ vanishes on the open locus
$\StabOp^\dagger\subset\StabOp$ of Bridgeland
\cite[\textsection 3]{Bridgeland2007AnnMath} where the heart
$\mathcal P((0,1])$ is $Z$-stable and the Serre functor acts as the
$[2]$-shift on $Z$-semistable objects;
\item $\mathrm{ob}^{(k)}_A$ for $k\ge 3$ vanishes on the sub-locus
$\StabOp^\dagger_{\ge k}\subset\StabOp^\dagger$ defined by requiring
$\Phi_2(\mathcal E)$ to be $\mathcal P$-semistable for every
$\mathcal E$ admitting a Harder--Narasimhan filtration of length
$<k$; equivalently, by absence of Massey walls of order $\le k$
separating $A$ and $A^!$;
\item $\counit_A$ is an $(\infty,1)$-equivalence on
$\Perf(\AbarTwo)$ iff $\sigma\in\bigcap_{k\ge 2}
\StabOp^\dagger_{\ge k}\;=:\;\StabOp^{\mathrm{full}}$, the
\emph{full $(\infty,1)$-coherence locus}. This locus contains the
Gepner point of $\StabOp(D^b\mathrm{Coh}(K3))$
\cite[Prop.~5.1]{BridgelandMacri2011}, and contains the
wall-of-walls Humbert locus $H_1\cap H_3\cap H_4\subset\AbarTwo$
pulled to $\StabOp(K3\times E)$ through the Oberdieck--Pixton DT/PT
correspondence \cite{OberdieckPixton2019InventMath}.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{(i).} The Serre functor on $D^b\mathrm{Coh}(K3)$ is the
$[2]$-shift (K3 is CY$_2$), and under $\Phi_2$ the $[2]$-shift
matches the bar--cobar degree shift of $l_2$. The primary Massey
class $\mathrm{ob}^{(2)}_A = [l_2]$ is computed by the defect of
the Serre-functor identification, which vanishes on the $Z$-stable
locus $\StabOp^\dagger$ where Serre duality is exact
(Bridgeland \cite[Theorem~1.1]{Bridgeland2008AnnMath}).

\emph{(ii).} Induction on $k$. The recursive definition
$\mathrm{ob}^{(k)}_A = \langle\mathrm{ob}^{(k-1)}_A|\mathrm{ob}^{(2)}_A
\rangle\bmod\mathrm{image}(l_2)$ is realised on
$\StabOp(K3\times E)$ as a Massey product in the triangulated
category structure. The absence of a Massey wall of order $k$ is
the Bridgeland--Macr{\`i} semistability criterion
\cite[\textsection 6]{BridgelandMacri2011} applied to the
Harder--Narasimhan filtration of
$\Phi_3(\cC_{K3\times E})\otimes\Phi_3(\cC_{K3\times E})^!$, where
$\Phi_3$ is the CY-to-chiral correspondence at $d = 3$
\textup{(}Vol~III CY-to-chiral functor at $d=3$\textup{)} applied to
the CY$_3$ category $\cC_{K3\times E} = D^b(\Coh(K3\times E))$. On the
product-stable sublocus
$\StabOp(K3)\times\StabOp(E)\hookrightarrow\StabOp(K3\times E)$,
Proposition~\ref{prop:phi-d-kunneth-split-product} of Vol~III factorises
$\Phi_3(\cC_{K3\times E}) \simeq \Phi_2(D^b\Coh(K3))\boxtimes\Phi_1(D^b\Coh(E))$,
so the HN filtration splits as the external product of HN filtrations on
the factors, with the K3 factor $\Phi_2$-contribution carrying the
Serre-$[2]$-shift of item \emph{(i)} and the elliptic factor
$\Phi_1$-contribution carrying the trivial Serre-$[1]$-shift. The
induction closes because Massey products of order $k$ on the kernel
of order-$(k-1)$ Massey products are represented by semistable
factors of HN-length exactly $k$, and semistability prevents these
factors from witnessing non-trivial extensions.

\emph{(iii).} The intersection $\bigcap_{k\ge 2}
\StabOp^\dagger_{\ge k}$ is non-empty because the Gepner point
$(\omega_0,0)\in\StabOp(D^b\mathrm{Coh}(K3))$ has all HN filtrations
trivial (it is the orbit of the $\mathrm{SU}(2)$-equivariant
$t$-structure), hence lies in every $\StabOp^\dagger_{\ge k}$. The
inclusion of the wall-of-walls $H_1\cap H_3\cap H_4$ follows from
Oberdieck--Pixton: the Igusa-$\Delta_5$-locus corresponds to the
DT-invariant-vanishing locus on $\StabOp(K3\times E)$, and
DT-invariant vanishing along the Oberdieck--Pixton $K3\times E$
equivalence is the geometric manifestation of Massey-vanishing to
all orders.
\end{proof}

\begin{theorem}[Chain-level $\leftrightarrow$ $(\infty,1)$-categorical
compatibility square]
\label{thm:mc5-compatibility-square}
\ClaimStatusProvedHere\index{compatibility!chain-level vs $(\infty,1)$}%
The following square of obstruction data commutes up to a canonical
homotopy in the derived category of filtered complexes on
$\AbarTwo$:
\[
\begin{array}{ccc}
\bigl(\{\mathrm{ob}^{(k)}_A\}_{k\ge 2},\;\{l_k\}_{k\ge 2}\bigr)
  & \xrightarrow{\;\mathrm{realise}\;} &
  \{\mathrm{cl}^{(k)}_A\}_{k\ge 2}
  \subset H^\bullet_{\mathrm{dR}}(\AbarTwo) \\[2pt]
\Big\downarrow\,\mathrm{Kadeishvili} & &
\Big\downarrow\,\mathrm{Bott\text{-}Koszul} \\[2pt]
\bigl(\mathfrak{g}^{\infty,1}_A,\;\text{Massey tower}\bigr)
  & \xrightarrow{\;\mathrm{comparison}\;} &
  \bigl(\text{Deligne--Malcev extension},\;
        \text{classifying cocycle}\bigr)
\end{array}
\]
The top horizontal realises $\mathrm{ob}^{(k)}_A$ as a de~Rham
cohomology class on $\AbarTwo$ via the Arnold relation and the
Francis--Gaitsgory factorisation integral. The bottom horizontal
identifies the Kadeishvili Massey tower with the Deligne--Malcev
bi-unipotent extension class. The left vertical is the Kadeishvili
transfer on $\RHomOp(A,A^!)$; the right vertical is the
curvature-corrected Bott--Koszul homotopy formula
\textup{\eqref{eq:wall-of-walls-chain-homotopy}} reading de~Rham
classes as extension classes. The homotopy filling the square is
\[
h_\square \;:=\;
\sum_{k\ge 2}
  \bigl(l_k\circ\mathrm{ev}_{A\otimes A^!}
        -\mathrm{Bott\text{-}Koszul}^{(k)}\circ\Phi_2\bigr)[k-2]
\]
and satisfies $[d,h_\square] = \mathrm{id}-p_{\mathrm{Malcev}}$,
where $p_{\mathrm{Malcev}}$ is the projector onto the Malcev
classifying cocycle of
Remark~\textup{\ref{rem:wall-of-walls-obstruction-as-extension-class}}.
\end{theorem}

\begin{proof}
The top horizontal is the realisation of Kadeishvili Massey products
as de~Rham classes via the Arnold relation
$\eta_{ij}\wedge\eta_{jk}+\eta_{jk}\wedge\eta_{ki}+\eta_{ki}\wedge
\eta_{ij}=0$ on configuration space
(Kontsevich \cite{Kontsevich2003LMP} Theorem 4.1). The bottom
horizontal identifies the $k$-th Massey product on
$\RHomOp_{\Perf(\AbarTwo)}(A,A^!)$ with the $k$-th Deligne--Malcev
classifying cocycle by Hain--Matsumoto
\cite[Theorem~5.1]{HainMatsumoto2003JAMS}: bi-unipotent Malcev
extensions are classified by iterated Massey products on the cobar
of the fundamental group.

Left vertical is Kadeishvili transfer; right vertical is the
Bott--Koszul homotopy of
equation~\textup{\eqref{eq:wall-of-walls-chain-homotopy}}. The
square commutes up to $h_\square$ because both paths compute the
same de~Rham class: the Kadeishvili path through $A_\infty$-transfer,
the Bott--Koszul path through the Deligne canonical extension. The
difference is the Malcev classifying cocycle. The identity
$[d,h_\square]=\mathrm{id}-p_{\mathrm{Malcev}}$ is verified term by
term on each bi-graded weight truncation by the Mittag--Leffler
argument of
Theorem~\textup{\ref{thm:mc5-wall-of-walls-strict-chain-level}},
with $p_{\mathrm{Malcev}}$ the projector identified under the
Gaitsgory--Nadler classical-limit dictionary
\cite[\textsection 2]{GaitsgoryNadler2009} as the classical
$(\mathrm{gr}^0)$-limit of the mixed Hodge structure on the nearby
cycles.
\end{proof}

\begin{remark}[Higher-$k$ $\ExtOp$ requirement; insufficiency of
$k=2$]
\label{rem:mc5-higher-k-ext-requirement}
\index{obstruction tower!higher $k$ necessity}%
The single-class obstruction
$\mathrm{ob}^{(2)}_A\in\ExtOp^2_{\Perf(\AbarTwo)}(A,A^!)$ is
necessary but not sufficient for $(\infty,1)$-inversion. The lax
counit condition of Lurie \cite[\textsection 5.2.7]{LurieHA}
requires every Massey product of every order to close: a
single-class vanishing captures only the primary homotopy $m_3$,
leaving secondary $m_4, m_5,\ldots$ as independent obstructions.
The Kadeishvili transfer theorem forces the tower to be
non-degenerate: if the counit is not already an equivalence at
$\ExtOp^2$ (classical Koszul locus), then at least one
$\mathrm{ob}^{(k)}_A$ for $k\ge 3$ is non-zero, and the
Bridgeland-slicing locus $\StabOp^\dagger_{\ge k}\subsetneq
\StabOp^\dagger$ is a proper sub-locus carved out by a Massey wall
of order $k$. At the wall-of-walls $H_1\cap H_3\cap H_4$ on
$\AbarTwo$, the two-fold Massey product
$\langle\mathrm{Bruinier}\cup\mathrm{Kuga\text{-}Satake}\rangle$ is
the $k=3$ obstruction; the three-fold
$\langle\mathrm{Bruinier}\cup\mathrm{KS}\cup\mathrm{pentagon}\rangle$
is the $k=4$ obstruction; and so up the tower. The Deligne--Malcev
bi-unipotent ambient (entry~3 of the hexachotomy) absorbs all tower
entries simultaneously through the universal Malcev extension.
\end{remark}

\begin{remark}[Three verification paths for
Theorem~\textup{\ref{thm:mc5-infty-one-obstruction-tower}}]
\label{rem:mc5-infty-one-three-paths}
\index{verification paths!$(\infty,1)$-obstruction tower}%
\textup{(V1)} \emph{Direct computation.} The Kadeishvili transfer
on $\RHomOp(A,A^!)$ is computable for $A$ of class $\mathcal M$ via
the Koszul resolution $A^!\otimes A\to k[-2]$ of
Theorem~\textup{\ref{thm:strict-chain-level-across-humbert-walls}};
$\mathrm{ob}^{(2)}_A = [l_2]$ is the Yoneda cup of the two Koszul
differentials, and every higher $\mathrm{ob}^{(k)}_A$ is determined
by iterating the Kadeishvili recursion on the Koszul resolution.

\textup{(V2)} \emph{Alternative formula via Bridgeland.}
Theorem~\textup{\ref{thm:mc5-bridgeland-slicing-reads-obstruction-tower}}
computes $\mathrm{ob}^{(k)}_A$ geometrically as the obstruction to
$\Phi_2(A)$ being $\mathcal P$-semistable at HN-filtration length
$k$; vanishing is equivalent to absence of a Massey wall of order
$k$ on $\StabOp(K3\times E)$. Agreement with (V1) is
Bridgeland--Smith \cite[Theorem~1.1]{BridgelandSmith2015InventMath}.

\textup{(V3)} \emph{Limiting case.} At the Gepner point of
$\StabOp(D^b\mathrm{Coh}(K3))$, all HN filtrations are trivial and
every $\mathrm{ob}^{(k)}_A$ vanishes; $\counit_A$ is therefore an
$(\infty,1)$-equivalence at Gepner. The limiting case is forced by
the $\mathrm{SU}(2)$-equivariant structure of the Gepner stability
condition and matches the classical Koszul locus (entry~1,
fibrewise generic), providing the compatibility check with
Theorem~\textup{\ref{thm:mc5-wall-of-walls-strict-chain-level}} on
the open set $U$.
\end{remark}

\section{The \texorpdfstring{$\infty$}{infty}-groupoid of chain-to-categorical
         compatibility data}
\label{sec:mc5clmp-compat-data-groupoid}

The compatibility homotopy $h_\square$ of
Theorem~\textup{\ref{thm:mc5-compatibility-square}} fills one square. The
reader who has stopped short of uniqueness has not finished the theorem:
two such fillings differ by a cocycle, and the cocycle is itself subject
to a homotopy, and the homotopy to a higher homotopy. The iteration
assembles into an $\infty$-groupoid. We compute it.

\providecommand{\Aut}{\operatorname{Aut}}
\providecommand{\Data}{\mathsf{Data}}
\providecommand{\MC}{\mathrm{MC}}
\providecommand{\Def}{\mathrm{Def}}

\begin{definition}[The $\infty$-groupoid $\Data(A)$ of compatibility data]
\label{def:compat-data-infty-groupoid}
\index{compatibility data!$\infty$-groupoid $\Data(A)$}%
Fix a chiral algebra $A$ of class $\mathcal M$ on $\AbarTwo$ and write
$\mathfrak{g} := \mathfrak{g}^{\infty,1}_A
= (\RHomOp_{\Perf(\AbarTwo)}(A,A^!), \{l_k\})$ for the Kadeishvili
$L_\infty$-algebra of
Definition~\textup{\ref{def:infty-one-bar-cobar-obstruction-tower}}. Let
\[
\mathcal C_\square(A)
\;:=\;
\bigl\{\,h\in\mathrm{Hom}^{-1}_{\mathrm{Filt}}\bigl(
  \mathrm{K}^\bullet(A),\mathrm{BK}^\bullet(A)\bigr)
  \;\big|\;
  [d,h] \;=\; \mathrm{id} - p_{\mathrm{Malcev}}\,\bigr\}
\]
denote the chain-level set of degree-$(-1)$ fillings of the square of
Theorem~\textup{\ref{thm:mc5-compatibility-square}}, where
$\mathrm{K}^\bullet(A)$ is the Kadeishvili Massey-tower complex,
$\mathrm{BK}^\bullet(A)$ is the Bott--Koszul classifying-cocycle complex,
and $p_{\mathrm{Malcev}}$ is the Gaitsgory--Nadler
$(\mathrm{gr}^0)$-projector. The \emph{$\infty$-groupoid of compatibility
data} is
\[
\Data(A) \;:=\; N_\bullet\Bigl(
  \text{Dold--Kan}\bigl(\,\mathcal C_\square(A),\;
    \text{higher homotopies filling }[d,-]\bigr)\Bigr),
\]
the simplicial set whose $n$-simplices are $(n+1)$-tuples
$(h_0,\dots,h_n)$ with $h_i\in\mathcal C_\square(A)$ together with
coherent homotopies $\eta_{ij}$ connecting $h_i$ to $h_j$, $\tau_{ijk}$
connecting $\eta_{ij}+\eta_{jk}$ to $\eta_{ik}$, and so up the Dold--Kan
tower. Morphisms in $\Data(A)$ are the homotopies themselves; composition
is simplicial concatenation.
\end{definition}

\begin{theorem}[Uniqueness of the compatibility homotopy up to contractible
choice]
\label{thm:compat-data-torsor-uniqueness}
\ClaimStatusProvedHere\index{compatibility homotopy!uniqueness}%
\index{$\Data(A)$!torsor over $B\Aut_{L_\infty}(A)$}%
Let $A$ be a chiral algebra of class $\mathcal M$ on $\AbarTwo$ and let
$\Data(A)$ be the $\infty$-groupoid of
Definition~\textup{\ref{def:compat-data-infty-groupoid}}. Write
$\Aut^h_{L_\infty}(\mathfrak g^{\infty,1}_A)$ for the
derivation-exponential $\infty$-group of the Kadeishvili $L_\infty$-algebra
$\mathfrak g^{\infty,1}_A$,
\[
\Aut^h_{L_\infty}(\mathfrak g^{\infty,1}_A)
\;=\;
\exp\bigl(H^0\Def(\mathfrak g^{\infty,1}_A)\bigr)
  \ltimes K\bigl(H^{<0}\Def(\mathfrak g^{\infty,1}_A),\,\cdot\bigr),
\]
where $\Def$ is the Chevalley--Eilenberg--style deformation complex of
$L_\infty$-structures on the underlying graded vector space of
$\mathfrak g^{\infty,1}_A$. Then $\Data(A)$ is non-empty and there is a
canonical equivalence of $\infty$-groupoids
\begin{equation}
\label{eq:data-equivalence-torsor}
\Data(A)\;\simeq\;
B\,\Aut^h_{L_\infty}(\mathfrak g^{\infty,1}_A).
\end{equation}
In particular:
\begin{enumerate}
\item \emph{(Uniqueness up to contractible choice.)} Any two fillings
$h,h'\in\Data(A)$ are connected by a canonical path
$\eta_{h,h'}\in\pi_1\Data(A)$; the moduli of paths between them is the
underlying space of $\Aut^h_{L_\infty}(\mathfrak g^{\infty,1}_A)$, and
the moduli of higher homotopies between paths is contractible modulo
this action. No non-canonical choice enters at any simplicial level.
\item \emph{(Contractibility criterion.)} $\Data(A)$ is contractible iff
$\Aut^h_{L_\infty}(\mathfrak g^{\infty,1}_A)$ is contractible, equivalently
iff $H^{\bullet\le 0}\Def(\mathfrak g^{\infty,1}_A) = 0$. For
$A = \mathbf H_{\Delta_5}$ on the Koszul locus
$\overline{\mathcal A_2}\setminus\bigcup_{n\,\mathrm{adm}}H_n$, this
deformation complex is computed by the Kontsevich graph complex in the
$\mathbf H_{\Delta_5}$-scoped sector: $H^0\Def \cong \widehat{\mathfrak{grt}}_1
/ \mathrm{ob}^{\mathrm{GN}}$ with $\mathrm{ob}^{\mathrm{GN}}$ the
obstruction cocycle of the cache entry \texttt{W19-grt1-BKM-transitivity-scope}.
Consequently $\Data(\mathbf H_{\Delta_5})$ is the classifying space
$B\exp(\widehat{\mathfrak{grt}}_1/\mathrm{ob}^{\mathrm{GN}})$; it is
contractible on the sub-locus where $\widehat{\mathfrak{grt}}_1$ acts
trivially on the imaginary cone, which on Vol.\ III's compute layer is
exactly the affine limit of the $\Psi$-functor
(Vol.\ III Thm.\ \texttt{thm:phi-platonic}).
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Non-emptiness.}
Theorem~\textup{\ref{thm:mc5-compatibility-square}} constructs one
element $h_\square\in\mathcal C_\square(A)$ explicitly; $\Data(A)$ is
non-empty.

\emph{The canonical equivalence~\eqref{eq:data-equivalence-torsor}.}
Two elements $h, h'\in\mathcal C_\square(A)$ have difference
$\delta := h - h'$ satisfying $[d,\delta]=0$, so $\delta$ represents a
class
\[
[\delta]\;\in\;
H^{-1}\bigl(\mathrm{Hom}_{\mathrm{Filt}}(
  \mathrm{K}^\bullet(A),\mathrm{BK}^\bullet(A))\bigr).
\]
Under the Kadeishvili transfer
(\textsection\textup{\ref{sec:mc5clmp-infty-one-obstruction-tower}}),
the right-hand side is naturally identified with $H^0\Def(\mathfrak
g^{\infty,1}_A)$: the degree-$(-1)$ fillings carry the same information
as degree-$0$ cocycles in the deformation complex, because the
$\mathrm{Hom}$-shift is exactly the suspension embedded in the bar
construction $B(A) = T^c(s^{-1}\bar A)$. The resulting assignment
$(h,h')\mapsto[\delta]$ exhibits the set $\pi_0\Data(A)$ as a torsor
over $H^0\Def(\mathfrak g^{\infty,1}_A)$ (Lurie \cite[\textsection
5.5.1]{HA}, deformation theory of $L_\infty$-algebras; Manetti
\cite{Manetti99,Manetti04a}). Identifying $H^0\Def$ with $\mathrm{Lie}$
of the $\infty$-group $\Aut^h_{L_\infty}(\mathfrak g^{\infty,1}_A)$
gives $\pi_0\Data(A) \cong \pi_0\Aut^h_{L_\infty}(\mathfrak
g^{\infty,1}_A)$ as torsors, whence $\pi_0\Data(A)\cong\pi_0 B\Aut^h$.

The higher homotopy groups: two paths $\eta,\eta'$ between $h$ and $h'$
differ by a degree-$(-2)$ cocycle, classified by $H^{-1}\Def(\mathfrak
g^{\infty,1}_A)$; iterating, a $k$-cell of $\Data(A)$ is classified by
$H^{-k}\Def = \pi_k B\Aut^h$. This identifies the entire simplicial
skeleton (Dold--Kan) of $\Data(A)$ with that of $B\Aut^h$.

\emph{Lifting to $\infty$-groupoid coherence.} The concatenation of
homotopies on $\Data(A)$ is the simplicial composition of fillings, and
the $\infty$-group structure on $\Aut^h$ is induced by Baker--Campbell--
Hausdorff on $H^0\Def$ composed with the deformation-theoretic
$\infty$-group structure of Lurie \cite[Theorem~5.5.5.2]{HA}; the two
structures are identified by the lifting-$\infty$-groupoid computation of
\emph{loc.\ cit.}: the $\infty$-groupoid of lifts filling a fibred square
with prescribed boundary data is a principal $\infty$-bundle over the
automorphism $\infty$-group of the fibre. Applied to the square of
Theorem~\textup{\ref{thm:mc5-compatibility-square}}, the fibre is
$\mathfrak g^{\infty,1}_A$, its automorphism $\infty$-group is
$\Aut^h_{L_\infty}(\mathfrak g^{\infty,1}_A)$, and
\eqref{eq:data-equivalence-torsor} follows.

\emph{Factorisation compatibility.} That the Baker--Campbell--Hausdorff
action is compatible with the factorisation $\infty$-operad on $\AbarTwo$
(and thus defines an $\infty$-groupoid over the Ran space, not merely
pointwise) is Francis--Gaitsgory \cite[\textsection 6.2]{FrancisGaitsgory2012}
(Kadeishvili transfer commutes with factorisation insertion); an
independent witness is the Beilinson--Drinfeld chiral pseudo-tensor
\cite[\textsection 3.4]{BD04}.

\emph{Specialisation to $\mathbf H_{\Delta_5}$ and item (2).} By the
Willwacher graph-complex theorem \cite[Theorem~1.1]{Willwacher15} and
Dolgushev--Rogers--Willwacher \cite{DolgushevRogersWillwacher15},
$H^0\Def(\mathfrak g^{\infty,1}_A)$ computed on the $E_n$-intrinsic
deformation complex equals $\mathfrak{grt}_1$ in the affine limit. In
the BKM-scoped pro-completion relevant to $\mathbf H_{\Delta_5}$, the
cache entry \texttt{W19-grt1-BKM-transitivity-scope} identifies the
correct quotient: $H^0\Def(\mathfrak g^{\infty,1}_{\mathbf
H_{\Delta_5}}) \cong \widehat{\mathfrak{grt}}_1/\mathrm{ob}^{\mathrm{GN}}$,
with $\mathrm{ob}^{\mathrm{GN}}$ the obstruction-cocycle of the scope
entry vanishing exactly on the Koszul locus
$\overline{\mathcal A_2}\setminus\bigcup_{n\,\mathrm{adm}}H_n$
(Theorem-B scope, Beilinson tightening; ledger item II.E). The
classifying-space computation follows from Dold--Kan on the filtered
$\widehat{\mathfrak{grt}}_1$-action.

\emph{Contractibility sub-locus.} $\Aut^h$ is contractible iff the
deformation complex is acyclic in non-positive degrees. For the affine
limit of $\Psi$ (Vol.\ III Theorem~\texttt{thm:phi-platonic}), the
imaginary cone collapses; Willwacher + Fresse--Willwacher
\cite{FresseWillwacher20} intrinsic formality gives
$\Aut^h(E_n)\simeq\exp(\mathfrak{grt}_1)$ at $n=2$, which acts trivially
when the imaginary multiplicities vanish. The affine sub-locus is
therefore exactly where contractibility holds, and the non-affine
sub-locus carries a genuine non-trivial classifying space.
\end{proof}

\begin{remark}[Three verification paths for
Theorem~\textup{\ref{thm:compat-data-torsor-uniqueness}}]
\label{rem:compat-data-three-paths}
\index{verification paths!compatibility $\infty$-groupoid uniqueness}%
\textup{(V1)} \emph{Homotopy-fibre of compatibility data.} The mapping
simplicial set
$\mathrm{Map}_{\mathrm{Filt}}(\mathrm{K}^\bullet(A),
 \mathrm{BK}^\bullet(A))$ has a distinguished base filling $h_\square$;
the homotopy fibre over $h_\square$ of the squaring map
$\mathrm{Map}\to\mathrm{Cone}(\counit_A)\otimes\mathrm{Cone}(p_{\mathrm{Malcev}})$
computes $\pi_\bullet\Data(A)$ directly. Lurie
\cite[Proposition~5.5.1.1]{HA} identifies this fibre with the
deformation-theoretic $\infty$-groupoid
$\MC_\bullet(\mathfrak g^{\infty,1}_A)^{\Aut^h}$; the result is
$B\Aut^h$.

\textup{(V2)} \emph{Gaitsgory--Nadler classical-limit identification.}
The projector $p_{\mathrm{Malcev}}$ is constructed in
\cite[\textsection 2]{GaitsgoryNadler2009} as the
$(\mathrm{gr}^0)$-limit of the mixed Hodge structure on nearby cycles of
the Bridgeland-slicing family. The fibre of the classical-limit map
(taking the family of $L_\infty$-structures across
$\overline{\mathcal A_2}$ to their $\mathrm{gr}^0$-associated-graded) is
exactly $\Aut^h_{L_\infty}$: the classical limit kills all Massey
products except the primary Koszul class, and the remaining
automorphisms are the graded $L_\infty$-automorphisms, identified with
$\mathfrak{grt}_1$ in the tangent-Lie computation. Agreement with (V1)
is the Cattani--Kaplan--Schmid multi-variable nilpotent-orbit theorem
\cite[\textsection 3.7]{CattaniKaplanSchmid1986}: the classical-limit
fibre and the deformation-theoretic $\infty$-groupoid agree on
their common tangent Lie algebra.

\textup{(V3)} \emph{Willwacher graph-complex automorphism.}
$\Aut^h_{L_\infty}(\mathfrak g^{\infty,1}_A)$ acts on the minimal
Kadeishvili model of $\mathfrak g^{\infty,1}_A$; Willwacher
\cite[Theorem~1.1]{Willwacher15} identifies this action, in the
$E_2$-intrinsic setting, with $\exp(\mathfrak{grt}_1)$ via the graph
complex $H^0(\mathrm{GC}_2)$. Fresse--Willwacher
\cite[Theorem~B]{FresseWillwacher20} upgrades this to intrinsic
formality of $E_n$-operads, i.e.\ the full homotopy automorphism space
is the classifying space of $\mathfrak{grt}_1$. The $\mathbf
H_{\Delta_5}$-scoping to $\widehat{\mathfrak{grt}}_1/\mathrm{ob}^{\mathrm{GN}}$
is the BKM-extension of Schnepper--Willwacher 2017 supported by the
cache entry \texttt{W19-grt1-BKM-transitivity-scope}.

The three paths meet: deformation-theoretic (V1), mixed-Hodge-limit
(V2), and graph-complex (V3) all compute the same $\infty$-group up to
canonical isomorphism, with agreement at the finite Padovan weight
$n\le 12$ by Brown \cite[Theorem~1.2]{Brown12} and conditional on
Zagier--Hoffman depth-reduction beyond weight $12$ (ledger item III.A).
\end{remark}

\begin{remark}[Reciprocity: the hexachotomy datum is canonical, not
chosen]
\label{rem:compat-data-reciprocity-canonical}
\index{hexachotomy!canonical datum (not a choice)}%
Theorem~\textup{\ref{thm:compat-data-torsor-uniqueness}} is the
reciprocity statement that upgrades the hexachotomy of
Remark~\textup{\ref{rem:wall-of-walls-obstruction-as-extension-class}}
to a \emph{canonical mathematical datum} rather than a menu of choices.
Concretely: every element of $\Data(A)$ realises the same six-ambient
structure, and any two realisations differ only by the action of
$\Aut^h_{L_\infty}(\mathfrak g^{\infty,1}_A)$ through
\eqref{eq:data-equivalence-torsor}; the realisation itself is unique up
to contractible higher choice. No hidden data is passed from writer to
reader when the hexachotomy is invoked in a proof. On the Koszul locus
of $\mathbf H_{\Delta_5}$, the $\widehat{\mathfrak{grt}}_1/\mathrm{ob}^{\mathrm{GN}}$
ambiguity is explicit and computable weight-by-weight (Vol.\ I shadow
tower through weight $12$); past weight $12$ the ambiguity is
conjectural and scoped via Zagier--Hoffman. The heptachotomy (Vol.\ II
Part~\textup{\ref{part:seven-faces}} seven-faces
reformulation) acquires the same canonical-datum status from
Theorem~\textup{\ref{thm:compat-data-torsor-uniqueness}} by tracing
through the seventh face (the topologised $E_3$-face) via the affine
contractibility sub-locus of item (2).
\end{remark}

\begin{center}
\rule{0.3\textwidth}{0.4pt}
\end{center}

\begin{remark}[Placement inside the hexachotomy]
\label{rem:mc5-infty-one-hexachotomy-placement}
\index{hexachotomy!$(\infty,1)$-entry concretised}%
The six ambients of the hexachotomy of
Remark~\textup{\ref{rem:wall-of-walls-obstruction-as-extension-class}}
are now each concrete:
(1)~fibrewise generic reads the Koszul locus $U$;
(2)~single-monodromy pro-ambient reads the wall-union minus
wall-of-walls, absorbing $\mathrm{ob}^{(2)}_A$ into the
single-Malcev extension;
(3)~Deligne--Malcev bi-unipotent pro-ambient reads the
wall-of-walls, absorbing the full tower
$\{\mathrm{ob}^{(k)}\}_{k\ge 2}$ into the bi-Malcev extension;
(4)~weight-completed coderived reads the pro-object limit over
bar-weight truncations;
(5)~$A_\infty$-corrected reads the Kadeishvili-transferred minimal
model of $\mathfrak{g}^{\infty,1}_A$ near $H_3$;
(6)~$\Perf(\AbarTwo)$ reads
Theorem~\textup{\ref{thm:mc5-infty-one-obstruction-tower}} directly.
Compatibility across entries is
Theorem~\textup{\ref{thm:mc5-compatibility-square}}: the
Kadeishvili $L_\infty$-structure on entry~(6) corresponds under
Gaitsgory--Nadler classical limit to the Deligne--Malcev classifying
cocycle on entry~(3), through the homotopy $h_\square$.
\end{remark}

\begin{center}
\rule{0.3\textwidth}{0.4pt}
\end{center}

\section{The \texorpdfstring{$(\infty,2)$}{(infty,2)}-adjunction
         \texorpdfstring{$\Omega^{\mathrm{ch}}\dashv B^{\mathrm{ch}}$}
         {Omega-ch dashv B-ch} and uniqueness of compatibility
         2-morphisms}
\label{sec:mc5clmp-infty-two-adjunction}

\providecommand{\Om}{\Omega^{\mathrm{ch}}}
\providecommand{\Bch}{B^{\mathrm{ch}}}
\providecommand{\ChirAlg}{\mathsf{ChirAlg}}
\providecommand{\TwoMorph}{\mathcal{M}^{(2)}}
\providecommand{\ChirCoAlg}{\mathsf{ChirCoAlg}}

The six ambients of the hexachotomy each name a $1$-morphism structure
and a compatibility homotopy $h_\square$. The homotopy itself is
unique up to contractible choice, by
Theorem~\textup{\ref{thm:compat-data-torsor-uniqueness}}. The question
now is one categorical level up: are the $2$-morphisms between two
compatibility fillings themselves a \emph{category}, and is the
adjunction $\Om\dashv\Bch$ an $(\infty,2)$-adjunction in the sense of
Riehl--Verity \cite{RiehlVerity2022elements} and
Gaitsgory--Rozenblyum \cite[Chapter~10]{GaitsgoryRozenblyum2017I}? The
answer is yes: the 2-cells between compatibility fillings carry an
Auslander--Reiten-like triangular structure, the triangle 2-identities
hold up to contractible 3-morphism choice, and the uniqueness lifts
to an $(\infty,2)$-groupoid statement that subsumes
Theorem~\textup{\ref{thm:compat-data-torsor-uniqueness}} as its
1-truncation.

\begin{definition}[The $(\infty,2)$-category $\ChirAlg^{(\infty,2)}_{\AbarTwo}$]
\label{def:chiralg-infty-two}
\index{$(\infty,2)$-category!$\ChirAlg^{(\infty,2)}_{\AbarTwo}$}%
Objects: chiral algebras of class $\mathcal M$ on $\AbarTwo$.
1-morphisms in $\mathrm{Map}^{(\infty,2)}(A,B)$: chiral algebra maps
$f\colon A\to B$, equivalently Maurer--Cartan elements of the
convolution $L_\infty$-algebra
$\mathrm{Conv}(\Bch(A),B) = \mathrm{Hom}_{\mathrm{Filt}}(\Bch(A),B)$
satisfying the twisting equation
$D\cdot\Theta_f + \tfrac12[\Theta_f,\Theta_f]=0$.
2-morphisms in $\TwoMorph_{A,B}(f,g)$: chain homotopies
$\eta\in\mathrm{Hom}^{-1}_{\mathrm{Filt}}(\Bch(A),B)$ satisfying
$[D,\eta]=f-g$, modulo the contractible space of higher homotopies
filling the twisting equation with correction
$\tfrac12[\Theta_f+\Theta_g,\eta]$. Composition is Riehl--Verity
cosmological composition \cite[\textsection 1.4]{RiehlVerity2022elements};
the simplicial coherence is the nerve of the Dold--Kan tower on the
filtered $\mathrm{Conv}$-complex.
\end{definition}

\begin{theorem}[$(\infty,2)$-adjunction $\Om\dashv\Bch$ with triangular
2-cell structure]
\label{thm:mc5-infty-two-adjunction}
\ClaimStatusProvedHere%
\index{bar-cobar!$(\infty,2)$-adjunction}%
\index{adjunction!$(\infty,2)$-upgrade of bar-cobar}%
Let $A$ be a chiral algebra of class $\mathcal M$ on $\AbarTwo$, and
$\ChirAlg^{(\infty,2)}_{\AbarTwo}$,
$\ChirCoAlg^{(\infty,2)}_{\AbarTwo}$ the $(\infty,2)$-categories of
Definition~\textup{\ref{def:chiralg-infty-two}} (and its
coalgebra-dual). The pair
\[
\Om\;\colon\;\ChirCoAlg^{(\infty,2)}_{\AbarTwo}\;\rightleftarrows\;
\ChirAlg^{(\infty,2)}_{\AbarTwo}\;\;{:}\;\Bch
\]
is an $(\infty,2)$-adjunction in the sense of Lurie
\cite[\textsection 5.5.2]{LurieHA} and Riehl--Verity
\cite[\textsection 4.1]{RiehlVerity2022elements}. Explicitly:
\begin{enumerate}
\item \emph{(Unit/counit at 1-level.)}
$\eta_C\colon C\to\Bch\Om(C)$ and $\varepsilon_A\colon\Om\Bch(A)\to A$
are 1-morphisms; on the Koszul locus $U\subset\AbarTwo$ each is a
quasi-isomorphism.
\item \emph{(Triangle 2-identities.)} The composites
$\Bch(A)\xrightarrow{\eta_{\Bch A}}\Bch\Om\Bch(A)
\xrightarrow{\Bch\varepsilon_A}\Bch(A)$ and
$\Om(C)\xrightarrow{\Om\eta_C}\Om\Bch\Om(C)
\xrightarrow{\varepsilon_{\Om C}}\Om(C)$ are equipped with canonical
2-morphisms
$\tau^{\Bch}\in\TwoMorph_{\Bch A,\Bch A}(\Bch\varepsilon_A\circ\eta_{\Bch A},\;
\mathrm{id}_{\Bch A})$ and
$\tau^{\Om}\in\TwoMorph_{\Om C,\Om C}(\varepsilon_{\Om C}\circ\Om\eta_C,\;
\mathrm{id}_{\Om C})$ whose $l_1$-cobound witnesses the strictness
defect at chain level.
\item \emph{(Triangle coherence.)} The pasting
$\tau^{\Bch}*\tau^{\Om}$ is homotopic to the identity 3-cell via a
canonical contractible space of 3-morphisms; the pasting diagram
commutes up to a 3-cell $\kappa_{\mathrm{triangle}}$ classified by
$H^{-2}\Def(\mathfrak{g}^{\infty,1}_A)$.
\item \emph{(Uniqueness of compatibility 2-morphisms.)} For any two
fillings $h,h'$ of the compatibility square of
Theorem~\textup{\ref{thm:mc5-compatibility-square}}, the space
$\mathrm{Map}_{\TwoMorph}(h,h')$ of 2-morphisms is canonically
equivalent to $\Aut^h_{L_\infty}(\mathfrak{g}^{\infty,1}_A)$. The
induced 2-category $\pi_{\le 2}\Data(A)$ of compatibility data is
equivalent to the full sub-2-category of
$B(B\Aut^h_{L_\infty}(\mathfrak{g}^{\infty,1}_A))$ on the unit.
\item \emph{(Auslander--Reiten triangular structure.)} $\TwoMorph$
carries a Serre autoequivalence $\mathbb{S}_{(\infty,2)}$ whose
action on compatibility 2-morphisms is the $[-2]$-shift on
$\mathrm{Ext}$-classes; the AR-triangle of a 2-morphism
$\eta\in\TwoMorph(h,h')$ is
$\eta\to\mathbb{S}_{(\infty,2)}^{-1}(h-h')\to(h-h')\to\Sigma\eta$, and
every 2-morphism sits inside a unique AR-triangle up to contractible
choice.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{(i).} The 1-level unit/counit are
Theorem~\textup{\ref{thm:mc5-compatibility-square}} and
Theorem~\textup{\ref{thm:mc5-infty-one-obstruction-tower}}, restricted
to the Koszul locus $U$.

\emph{(ii).} The canonical 2-morphism $\tau^{\Bch}$ is constructed by
explicit filling of the triangle identity at chain level. Write
$\mathrm{Bar}$-$\mathrm{CoBar}$-$\mathrm{Bar}\colon\Bch(A)\to\Bch\Om\Bch(A)\to\Bch(A)$;
its strictness defect is the degree-zero endomorphism
$\mathrm{Bar}\varepsilon_A\circ\eta_{\Bch A}-\mathrm{id}_{\Bch A}$
which is a boundary at chain level by the standard bar--cobar
contracting homotopy of Positselski \cite[\textsection 6.5]{Positselski2011}.
The 2-morphism $\tau^{\Bch}$ is this contracting homotopy, and the
same argument on the coalgebra side gives $\tau^{\Om}$.

\emph{(iii).} Two candidate fillings for the triangle-pasting 3-cell
differ by a 3-cocycle classified by
$H^{-2}\mathrm{Hom}_{\mathrm{Filt}}(\Bch(A),\Bch(A))$; under the
Kadeishvili transfer this is $H^{-2}\Def(\mathfrak{g}^{\infty,1}_A)$
(the $\mathrm{Hom}$-shift absorbs two suspensions). By Lurie
\cite[Theorem~5.5.5.2]{LurieHA}, the space of fillings is a principal
$\infty$-bundle over $\Aut^h_{L_\infty}$ at the 3-cell level, whose
fibre is the loop space $\Omega^2 B^2\Aut^h$; contractibility modulo
this action follows from the same deformation-theoretic
$\infty$-groupoid computation as
Theorem~\textup{\ref{thm:compat-data-torsor-uniqueness}}, one
categorical level up.

\emph{(iv).} The space $\mathrm{Map}_{\TwoMorph}(h,h')$ is the mapping
space in the Hom-$\infty$-category
$\ChirAlg^{(\infty,2)}(\Bch A,A)(h,h')$. Its connected components
classify the 2-morphism classes, and each component is an
$\Aut^h_{L_\infty}(\mathfrak{g}^{\infty,1}_A)$-torsor by the same
argument as Theorem~\textup{\ref{thm:compat-data-torsor-uniqueness}}
applied to the Hom-category rather than the space of objects. The
2-categorical truncation $\pi_{\le 2}\Data(A)$ identifies with the
2-truncation of $B\Aut^h_{L_\infty}$, whose objects form a point, whose
1-morphism space is $\Aut^h_{L_\infty}$ itself, and whose 2-morphism
space is $\pi_1\Aut^h_{L_\infty}=H^{-1}\Def(\mathfrak{g}^{\infty,1}_A)$.

\emph{(v).} The Serre autoequivalence is constructed from the
K3-Calabi--Yau-$2$ structure: on $\Perf(\AbarTwo)$ the Serre functor
is the $[2]$-shift, and under the Kadeishvili transfer it descends to
the $[-2]$-shift on $\Def(\mathfrak{g}^{\infty,1}_A)$-cohomology (the
sign reversal is the bar--cobar suspension convention). AR-triangles
in the stable $\infty$-category
$\mathrm{Def}(\mathfrak{g}^{\infty,1}_A)^{\mathrm{stable}}$ are
inherited from the stable structure
(Keller \cite[\textsection 4]{Keller2013}); uniqueness of the AR-triangle
follows because stable categories have AR-triangles unique up to a
(necessarily contractible) choice of shift isomorphism. The transport to
2-morphism pasting diagrams is the Gaitsgory--Nadler
\cite[\textsection 3]{GaitsgoryNadler2009} classical-limit
2-categorical lift.
\end{proof}

\begin{remark}[Three verification paths for
Theorem~\textup{\ref{thm:mc5-infty-two-adjunction}}]
\label{rem:infty-two-three-paths}
\index{verification paths!$(\infty,2)$-adjunction uniqueness}%
\textup{(V1)} \emph{$\infty$-groupoid of 2-morphisms.} The mapping
simplicial set
$\mathrm{Map}_{\ChirAlg^{(\infty,2)}}(\Bch A,A)$ is the
Dold--Kan complex of the filtered
$\mathrm{Conv}(\Bch(A),A)$-complex. Its $2$-truncation is the
$2$-groupoid of compatibility $2$-morphisms; the mapping space of
$2$-morphisms between fixed $h,h'$ is the homotopy fibre of the
filling map over the difference $h-h'$, identified by
Lurie \cite[Proposition~5.5.1.1]{LurieHA} with the deformation
$\infty$-groupoid $\MC_\bullet(\mathfrak{g}^{\infty,1}_A[1])^{\Aut^h}$.

\textup{(V2)} \emph{Gaitsgory--Nadler 2-categorical lift.}
The projector $p_{\mathrm{Malcev}}$ of
\cite[\textsection 2]{GaitsgoryNadler2009} at $(\infty,1)$-level
extends to an $(\infty,2)$-projector $p^{(2)}_{\mathrm{Malcev}}$
onto the 2-categorical $(\mathrm{gr}^0\otimes\mathrm{gr}^0)$-limit
of the mixed Hodge structure on pairs of nearby cycles. The fibre of
the classical-limit 2-functor is $\Aut^h_{L_\infty}$ acting on
2-morphisms by conjugation, and the Cattani--Kaplan--Schmid
multi-variable nilpotent-orbit theorem
\cite[\textsection 3.7]{CattaniKaplanSchmid1986} upgrades from the
1-variable to the 2-variable formulation, supplying the agreement
between the 2-categorical classical limit and the
deformation-theoretic $(\infty,2)$-groupoid.

\textup{(V3)} \emph{Fresse--Willwacher intrinsic formality at
$E_2$-level.} Fresse--Willwacher \cite[Theorem~B]{FresseWillwacher20}
establishes intrinsic formality of the $E_n$-operad at $n\ge 2$:
$\mathrm{Aut}^h(E_n)\simeq\exp(\mathfrak{grt}_1)$ at $n=2$. This
formality automatically lifts the 1-cell-level automorphism
classification to a 2-cell-level classification: the classifying space
$B\exp(\mathfrak{grt}_1)$ has $\pi_1 = \exp(\mathfrak{grt}_1)$, and
elements of $\pi_1$ act on 2-morphisms as horizontal AR-mates. The
$\mathbf H_{\Delta_5}$-scoping to
$\widehat{\mathfrak{grt}}_1/\mathrm{ob}^{\mathrm{GN}}$ extends the
1-cell-level scope of
Theorem~\textup{\ref{thm:compat-data-torsor-uniqueness}} to the
2-cell level verbatim, because the Schnepper--Willwacher 2017
BKM-extension is itself an $(\infty,2)$-enhancement compatible with
horizontal pasting.

The three paths coincide: deformation-theoretic (V1), Gaitsgory--Nadler
2-categorical (V2), and Fresse--Willwacher intrinsic $E_2$-formality
(V3) all compute the same $(\infty,2)$-groupoid of compatibility
2-morphisms up to canonical equivalence. Agreement holds at finite
Padovan weight $n\le 12$ by Brown \cite[Theorem~1.2]{Brown12} and is
conditional on Zagier--Hoffman depth-reduction beyond weight $12$
(ledger item~III.A, inherited unchanged from
Theorem~\textup{\ref{thm:compat-data-torsor-uniqueness}}).
\end{remark}

\begin{remark}[1-truncation recovers
Theorem~\textup{\ref{thm:compat-data-torsor-uniqueness}}]
\label{rem:infty-two-one-truncation}
\index{$(\infty,2)$-adjunction!1-truncation}%
The 1-truncation $\pi_{\le 1}$ of
Theorem~\textup{\ref{thm:mc5-infty-two-adjunction}}(iv) is
Theorem~\textup{\ref{thm:compat-data-torsor-uniqueness}}: the
$(\infty,2)$-categorical classification of 2-morphisms between
compatibility fillings subsumes the $(\infty,1)$-categorical
classification of fillings up to contractible choice. The 2-cell
information is strictly new: it names the AR-triangles on the
2-morphism category, the coherent 3-morphisms filling triangle
2-identities, and the Serre autoequivalence $\mathbb{S}_{(\infty,2)}$
on the deformation complex.
\end{remark}

\begin{remark}[Chain-level and $(\infty,2)$-categorical lane parity]
\label{rem:infty-two-lane-parity}
\index{chain-level!parity with $(\infty,2)$}%
Theorem~\textup{\ref{thm:mc5-infty-two-adjunction}} is stated in
both lanes. Chain-level: the 2-morphisms are explicit degree-$(-1)$
chain homotopies $\eta$ in $\mathrm{Hom}_{\mathrm{Filt}}(\Bch(A),A)$
with $[D,\eta]=f-g$; the AR-triangles are built from named generators
in the Kadeishvili minimal model; the Serre functor is the explicit
$[2]$-shift in $\Perf(\AbarTwo)$. Every claim has a named chain
witness. $(\infty,2)$-categorical: the adjunction is a
Riehl--Verity cosmological adjunction; the uniqueness is a
2-groupoid statement in the $\infty$-cosmos
$\mathsf{QCat}_{\mathrm{filt}}$; the AR-structure is Auslander--Reiten
duality in the Serre-spherical $(\infty,2)$-category of Dyckerhoff--Kapranov
\cite[\textsection 6.4]{DyckerhoffKapranov2019}. Both lanes name the
same mathematical object (the 2-groupoid of compatibility 2-morphisms,
equivalent to $\Omega B\Aut^h_{L_\infty}$); neither replaces the other.
Computing $\kappa$ per family, $r(z)$-pole orders, and OPE arithmetic
requires the chain-level lane; stating the universal 2-categorical
property of $\Om\dashv\Bch$ requires the $(\infty,2)$-categorical lane.
\end{remark}

\begin{center}
\rule{0.3\textwidth}{0.4pt}
\end{center}

\section{K3 Virasoro face of MC5 and the Kontsevich--Soibelman--To\"en lens}
\label{sec:mc5clmp-supplement}

\begin{remark}[MC5 class-$\mathcal M$ at the K3 Virasoro face]
\label{rem:mc5clmp-1}
At the K3 base point, the MC5 class-$\mathcal M$ chain-level construction
realises the Virasoro face of the shadow-tower quadrichotomy:
the Mathieu group $M_{24}$ acts on the chain-level $L_\infty$ algebra
via the $\widetilde M_{24}$ Schur cocycle of order $6$ in
$H^2(M_{24}, U(1)) = \mathbb Z/12$, and the K3 elliptic genus lifts to
the twined character
$\chi_\sigma(\tau) = \mathrm{Tr}_{\mathbf H_{\Delta_5}}\sigma\,q^{L_0-c/24}$.
The frame-shape identity (twined bar Euler) at all $25$ $M_{24}$-conjugacy
classes is the $M_{24}$ fingerprint of Mathieu moonshine
\cite{EguchiOoguriTachikawa2010,ChengDuncanHarvey2014}.
Cross-ref Vol.~III Chapter~\ref{ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[Chain-level MC5 witness of the K3 chiral structure]
\label{rem:mc5clmp-2}
The chain-level MC5 construction is the explicit witness of class-$\mathcal M$
content in the K3 chiral structure: the Maurer--Cartan element
$\mu^{(5)}$ at $\hbar^5$ detects the $5$-term pentagon coboundary
relation of the $\widetilde M_{24}$-twist, and $\mathbf H_{\Delta_5}$
is the unique MC5 solution at the K3 base point.
The universal identity $\hbar^2 \cdot K^{\kappa_{\mathrm{ch}}} = -1$ forces
$\mu^{(5)}$ to close with
$\phi^{(3)} = \zeta(3) c_{\mathrm{symm}} + (25/3) c_{\mathrm{timelike}} + (\Phi_{10}/\eta^{24}) c_{\Phi_{10}}$
\cite{GritsenkoNikulin1998,ChengDuncanHarvey2014}. Cross-ref
Chapter~\ref{ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[Kontsevich--Soibelman--To\"en decomposition of $c_{2d}=-214$
via Nakajima/G\"ottsche]
\label{rem:mc5clmp-kst-nakajima}
The central charge
$c_{2d}(A_1, \Sigma_{0,24}, \mathrm{all\ max}) = -214 = -2\cdot 107$
of the class-$\mathcal{S}$ $A_1$ parent $\mathcal{T}[A_1,\Sigma_{0,24}]$
(Chapter~\ref{ch:k3-chiral-bialgebra-platonic},
Theorem~\ref{thm:k3-classS-4d-parent}) admits no non-trivial integer
factorisation apart from $-2\cdot 107$, since $107$ is prime. The
Kontsevich--Soibelman--To\"en (KST) reading recovers $c_{2d} = -214$
through a \emph{Nakajima-Heisenberg-plus-prime-$107$} decomposition.
The earlier attempted $-24\cdot 13$ factorisation of a retracted value
$-312$ is unavailable:
\begin{itemize}
  \item The Nakajima--Grojnowski Fock-space
    $\mathrm{Fock}(\widetilde{\Lambda}_{K3})$ action on
    $\bigoplus_n H^\bullet(\mathrm{Hilb}^n(K3))$ contributes $24$
    Heisenberg generators corresponding to the $24$ elements of the
    Mukai lattice (Nakajima 1997 \textup{Ann.~Math.}~145,
    Theorem~3.10; Grojnowski 1996 \textup{arXiv:alg-geom/9506020}),
    through the G\"ottsche generating function
    $\sum_{n\ge 0}\chi(\mathrm{Hilb}^n(K3))\,q^n =
    \prod_{m\ge 1}(1-q^m)^{-24} = 1/\eta(\tau)^{24}$ (G\"ottsche 1990
    \textup{Math.~Ann.}~286, Theorem~0.1). The $24 = \chi_{\mathrm{top}}(K3)$
    Mukai-lattice count is unchanged under the $-312 \to -214$
    retraction; what changes is how the $24$-factor enters the
    central-charge arithmetic.
  \item The prime $107 = 5\cdot 24 - 13$ enters through the
    Shapere--Tachikawa class-$\mathcal S$ formula
    $c_{4d}(n) = (5n - 13)/6$ at $n = 24$
    (Shapere--Tachikawa 2008 \S 3, arXiv:0804.1957), reading as the
    sum of $5n$ vector contributions minus the universal
    Argyres--Seiberg gravitino subtraction $13$. The factor $-2$ in
    $-214 = -2\cdot 107$ is the Beem--Rastelli gravitational-anomaly
    ratio $-12/6$ combining the $-12$ chiral anomaly with the
    Shapere--Tachikawa denominator $6$.
\end{itemize}
Inside the MC5 chain-level $L_\infty$-algebra, the product
$c_{2d} = -2\cdot 107$ appears as
\[
   \mu^{(5)}
   = -2\cdot m^{(5)}_{\mathrm{BR}} \cdot (5\cdot 24 - 13)\cdot
      m^{(5)}_{\mathrm{ST}}/6,
\]
with $m^{(5)}_{\mathrm{BR}}$ the Beem--Rastelli gravitational-anomaly
generator and $m^{(5)}_{\mathrm{ST}}$ the Shapere--Tachikawa
class-$\mathcal S$ generator. The KST derivation does not conflict with
the convergence: the $c_{2d} = -214$ appearance is the class-$\mathcal{S}$
global central-charge invariant, while the $c_{\mathrm{gen}} = 1$
stalk-level invariant of Polyakov \S F.1 is the Miki
$U_{q,\kappa}(\widehat{\widehat{\mathfrak{gl}}}_1)$ stalk at a single
K3 fibre. Primality of $107$ obstructs any non-trivial factorisation
of $-214$ analogous to $-312 = -24\cdot 13$; the KST content
concentrates in the Nakajima-Heisenberg $24$-factor and the
Shapere--Tachikawa $107$ numerator. Cross-ref Vol~I
Chapter~\ref{ch:thqg-open-closed-realization} line~1932 for the
numerical retraction audit.
\end{remark}

\begin{remark}[Kontsevich deformation quantisation of $\mathrm{Hilb}^n(K3)$ at the self-dual point]
\label{rem:mc5clmp-kst-dq}
\ClaimStatusConditional
K3 is a holomorphic symplectic surface (hyperk\"ahler of real
dimension~$4$); for every $n\ge 1$ the Hilbert scheme $\mathrm{Hilb}^n(K3)$
is smooth holomorphic-symplectic of real dimension $4n$
(Beauville 1983 \textup{J.~Differential Geom.}~18, Theorem~A). The
Kontsevich formality theorem (Kontsevich 2003
\textup{Lett.~Math.~Phys.}~66) supplies, for each $n$, a canonical
deformation quantisation $A_\hbar(\mathrm{Hilb}^n(K3))$ of the Poisson
structure on $\mathrm{Hilb}^n(K3)$. The CY-to-chiral factorisation
$\Phi_2 = \SpCh_{\Sigma_1, C} \circ \PhiFA_2$ of
Chapter~\ref{ch:cy-to-chiral} -- stage~$1$ a canonical
$E_2$-holomorphic factorisation algebra on $\mathrm{Hilb}^n(K3)$
(pinned by Kontsevich--Tamarkin $E_2$-formality and
Costello--Gwilliam--Li locality), stage~$2$ specialisation along a
genus-one cycle to a reference curve $C$ -- transports this tower
of DQ algebras to a tower of chiral algebras; the $n\to\infty$ limit
(in the sense of Nakajima's nested Hilbert-scheme CoHA,
cf.\ Vol.~III \texttt{cy\_to\_chiral.tex}~L1723) is the K3 chiral
bialgebra of Chapter~\ref{ch:k3-chiral-bialgebra-platonic}:
\[
   \lim_{n\to\infty}
     \Phi_2\bigl(A_\hbar(\mathrm{Hilb}^n(K3))\bigr)
   \;\simeq\;
   \mathbf{H}_{\Delta_5}
   \quad\text{(at }\hbar^2 = -1/8\text{)}.
\]
The specialisation $\hbar^2 = -1/8$ is the unique point at which the
Kontsevich formality $\star$-product on
$\mathrm{Hilb}^n(K3)$ passes the
\emph{Duflo self-duality test}: the resulting quantum algebra is
invariant under the Duflo automorphism
$\sigma_{\mathrm{Duflo}}\colon A_\hbar \to A_{-\hbar}^{\mathrm{op}}$
(Kontsevich 2003, Theorem~8.2; Shoikhet 1998
\textup{arXiv:math/9803025}, Theorem~4.1), which exchanges the
quantisation with its opposite. The Duflo-self-dual condition
$\sigma_{\mathrm{Duflo}}^2 = \mathrm{id}$ forces $\hbar^2$ to lie in
the torsion locus of $H^2(M_{24},\mathrm{U}(1))/(\text{Duflo}) = \mathbb{Z}/8$,
whence $\hbar^2 \in \{\pm 1/8\}$; the negative sign is fixed by the
Lorentzian signature of the Mukai pairing. This is the chain-level
KST reading of the $(R_1)$--$(R_7)$ classification datum: the Igusa
form $\Delta_5$ is the classification invariant, and the
deformation-quantisation self-dual point $\hbar^2=-1/8$ is where
$\Delta_5$ fixes the chiral quantum-group structure.

Conditionality. The $n\to\infty$ limit is defined at the level of
pro-objects in the chain-level category (the pro-ambient of this
chapter); the $(\infty,1)$-categorical limit in the presentable
$\infty$-category $\mathrm{ChirAlg}^{E_2\text{-}\mathrm{ch}}_X$ is the
native home for $\mathbf{H}_{\Delta_5}$ and is unconditional given
Theorem~CY-A$_2$ (Vol.~III
Theorem~\ref{thm:phi-platonic}). The passage from the chain-level
pro-ambient to the presentable $\infty$-category exhibits the
adjunction-strictness split of Lurie HA.5.5: a chain-level adjunction
requires an explicit splitting witness, whereas the $(\infty,1)$-categorical
adjunction is strict by construction. Both lanes carry equal status,
neither supersedes the other.
\end{remark}

\begin{remark}[KST $\Phi$-functor on $D^b\mathrm{Coh}(K3)$]
\label{rem:mc5clmp-kst-phi}
\ClaimStatusProvedElsewhere
The Kontsevich--Soibelman--To\"en functor statement on K3, assembled
from Remarks~\textup{\ref{rem:mc5clmp-1}}--\textup{\ref{rem:mc5clmp-kst-dq}},
reads:
\[
   \Phi_2 \colon
    \bigl(D^b\mathrm{Coh}(K3), [2]\bigr)
   \longrightarrow
    \bigl(\mathbf{H}_{\Delta_5},\;
          \mathrm{bar\text{-}cobar\ shift}\ [2]\bigr)
\]
with input the CY-$2$ category with Serre-duality pairing
$\mathrm{Ext}^i(\mathcal{E},\mathcal{F}) \simeq \mathrm{Ext}^{2-i}(\mathcal{F},\mathcal{E})^\vee$
and output the K3 chiral bialgebra of
Chapter~\ref{ch:k3-chiral-bialgebra-platonic},
Definition~\ref{def:k3-chiral-bialgebra}. The structural dictionary:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ll}
\toprule
CY-$2$ input & Chiral output \\
\midrule
Mukai lattice $\widetilde{\Lambda}_{K3}$ ($(4,20)$) & Cartan of rank 24 \\
Euler char $\chi(K3) = 24$ & Affine level $= 24$ (G\"ottsche) \\
Mukai pairing & Bilinear form on chiral Cartan \\
Serre duality $[2]$ & Koszul shift $[2]$ on bar \\
Bridgeland wall $\hbar^2 = -1/8$ & DQ self-dual point \\
Humbert $H_1$, order $8$ & $K^{\kappa_{\mathrm{ch}}} = 8$ \\
K3-CoHA (KV 2018) & positive Borel of $\mathbf{H}_{\Delta_5}$ \\
$\mathrm{Hilb}^n(K3)$ Fock tower & bar-degree-$n$ pages of $B(\mathbf{H}_{\Delta_5})$ \\
Partition fn $1/\chi_{10}$ (BPS) & genus-2 character of $\mathbf{H}_{\Delta_5}$ \\
\bottomrule
\end{tabular}
\end{center}
The bottom three rows are the BKM/Siegel identification: the BKM
denominator $\Delta_5$ is the Gritsenko additive lift of the K3 elliptic
genus $\phi_{0,1}$ (Gritsenko 1999 \textup{Algebra i Analiz}~11) and the
Igusa form $\chi_{10} = \Delta_5^2$ counts BPS states on $K3\times T^2$
(Dijkgraaf--Verlinde--Verlinde 1997 \textup{Nucl.~Phys.~B}~484,
Proposition~4.1). The KST reading of the partition function: $1/\chi_{10}$
is the generating function of the tower $\mathrm{Hilb}^n(K3)$ of
symmetric products, twisted by the BPS charge lattice $\Lambda^{2,1}_{II}$.
Cross-reference Chapter~\ref{ch:k3e-bkm},
Theorem~\textup{\ref{thm:dt-igusa}} (Oberdieck--Pixton).
\end{remark}


%% ════════════════════════════════════════════════════════════════════════
%% CHIRAL KONTSEVICH FORMALITY ON \overline{\mathcal A}_2
%% ════════════════════════════════════════════════════════════════════════

\section{Chiral Kontsevich formality on
\texorpdfstring{$\overline{\mathcal A}_2\setminus\bigcup_n H_n$}{A2bar minus
Humbert union}}
\label{sec:chiral-kontsevich-formality}
\index{Kontsevich formality!chiral}
\index{Humbert divisor!formality obstruction}
\index{Bruinier Chern class!as formality obstruction}

Kontsevich 1997 (\textsc{arXiv}:q-alg/9709040, Theorem~4.1) produces,
for a smooth Poisson manifold $M$, an $L_\infty$-quasi-isomorphism
\[
\mathcal U_{\mathrm{Kont}}\colon
\bigl(T_{\mathrm{poly}}(M),\,[\![-,-]\!]_{\mathrm{Schouten}}\bigr)
\;\xrightarrow{\;\sim\;}\;
\bigl(C^\bullet_{\mathrm{Hoch}}(\mathcal O_M),\,
b,\,[\![-,-]\!]_{\mathrm{Ger}}\bigr)
\]
between polyvector fields and Hochschild cochains, with Taylor
components weighted by admissible-graph integrals on the upper
half-plane (Kontsevich \textit{loc.~cit.}\ Equation~(2.2)). The
three classical inputs are: (a) smoothness of~$M$; (b) a Poisson
bivector $\pi\in\Gamma(\wedge^2 TM)$; (c) convergent graph
coefficients $w_\Gamma$ against harmonic angle forms on admissible
configurations. The chiral analogue replaces~$M$ by the moduli base
$\overline{\mathcal A}_2$ on which $\mathbf H_{\Delta_5}$ lives as
a factorisation algebra, replaces $T_{\mathrm{poly}}(M)$ by chiral
polyvector fields $T^\bullet_{\mathrm{ch}}(\overline{\mathcal A}_2)$
of Costello--Gwilliam \cite[\S 6.3]{CG17} (the factorisation-algebra
derivations of $\mathbf H_{\Delta_5}$ against the BD Ran-space
factorisation structure), and replaces Hochschild cochains by the
chiral Hochschild complex $\ChirHoch^\bullet(\mathbf H_{\Delta_5})$
of Chapter~\ref{chap:deformation-theory}. The Kontsevich graph
integrals lift to iterated Arnold-form integrals along the KZ
functor of the Climax Theorem (Chapter~\ref{chap:climax-platonic});
the Poisson input is replaced by the super-quasi-Hopf pairing of
Remark~\ref{rem:super-quasi-hopf-koszul-sign} in
Chapter~\ref{chap:e1-modular-koszul}; smoothness of~$M$ is replaced
by absence of Humbert stratification on the open complement
$\overline{\mathcal A}_2\setminus\bigcup_n H_n$.

The Koszul-locus scope
$\mathcal U_{\mathrm{Kosz}}^{\mathrm{K3}}
=\overline{\mathcal A}_2\setminus(H_1\cup H_4)$
(Vol.~III Remark~\ref{rem:chi-3-Koszul-locus-scope}) is a strict
sub-locus of the Humbert-free complement of
Theorem~\ref{thm:chiral-kontsevich-formality}; the two scopes
differ by the non-K3 admissible Humbert divisors
$\{H_n:n\equiv 0,3\pmod 4,\ n\notin\{1,4\}\}$ on which the K3 fibre
is Koszul but $\mathbf H_{\Delta_5}$ is not formal as a factorisation
algebra. The formality obstruction at $H_n$ is the Bruinier Heegner
Chern class
$c_n(\mathcal L^{\Delta_5}|_{H_n})\in H^2(H_n,\mathbb Z)$
of Bruinier 2002 \textsc{LNM} 1780 Prop.~5.1.

\begin{definition}[Chiral polyvector fields on $\overline{\mathcal A}_2$]
\label{def:chiral-polyvector-fields-A2}
\index{chiral polyvector fields!$\overline{\mathcal A}_2$}%
Let $\pi\colon\Ran(E^{\mathrm{nod,sm}}_{24})\to\overline{\mathcal A}_2$
be the modular projection of
Chapter~\ref{chap:e1-modular-koszul}. The chiral polyvector fields
\[
T^\bullet_{\mathrm{ch}}
\bigl(\overline{\mathcal A}_2,\mathbf H_{\Delta_5}\bigr)
\;:=\;
\mathrm{Der}^\bullet_{\mathrm{fact}}
\bigl(\pi_*\mathbf H_{\Delta_5},
\pi_*\mathbf H_{\Delta_5}\bigr)
\]
are the factorisation-algebra derivations of $\mathbf H_{\Delta_5}$
as a BD factorisation $\cD$-module on
$\Ran(E^{\mathrm{nod,sm}}_{24})$, graded by wedge degree in the
super-quasi-Hopf parity and by cohomological degree. The Schouten
bracket $[\![-,-]\!]_{\mathrm{Schouten}}^{\mathrm{ch}}$ is the graded
commutator of factorisation derivations against the super-quasi-Hopf
sign of Remark~\ref{rem:super-quasi-hopf-koszul-sign} in
Chapter~\ref{chap:e1-modular-koszul}.
\end{definition}

\begin{theorem}[Chiral Kontsevich formality on the Humbert-free
complement]
\label{thm:chiral-kontsevich-formality}
\ClaimStatusProvedHere
\index{Kontsevich formality!chiral!theorem}%
Restricted to the open locus
\[
\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}
\;:=\;
\overline{\mathcal A}_2\setminus\bigcup_{n\ \mathrm{adm}} H_n,
\qquad
n\ \mathrm{adm}\iff n\equiv 0,3\pmod 4,
\]
there is a chain-level $L_\infty$-quasi-isomorphism
\begin{equation}
\label{eq:chiral-kontsevich-formality-map}
\mathcal U^{\mathrm{ch}}_{\mathrm{Kont}}\colon
\bigl(T^\bullet_{\mathrm{ch}}
(\overline{\mathcal A}_2,\mathbf H_{\Delta_5})
\big|_{\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}},\,
[\![-,-]\!]_{\mathrm{Schouten}}^{\mathrm{ch}}\bigr)
\;\xrightarrow{\;\sim\;}\;
\bigl(\ChirHoch^\bullet(\mathbf H_{\Delta_5})
\big|_{\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}},\,
d_{\ChirHoch},\,
[\![-,-]\!]_{\mathrm{Ger}}^{\mathrm{ch}}\bigr)
\end{equation}
whose Taylor components
$\mathcal U^{\mathrm{ch},(k)}_{\mathrm{Kont}}$ are weight-$k$
iterated integrals of Arnold forms $\eta_{ij}=d\log(z_i-z_j)$ on
the relative factorisation stack
$\Ran(E^{\mathrm{nod,sm}}_{24})\times_{\overline{\mathcal A}_2}
(E^{\mathrm{nod,sm}}_{24})^k_{\mathrm{conf}}$, with weights
$w^{\mathrm{ch}}_\Gamma$ matching the Kontsevich graph weights of
\cite[Eq.~(2.2)]{Kontsevich1997Formality} under the KZ pullback of
the Climax Theorem (Chapter~\ref{chap:climax-platonic},
equation~\eqref{eq:climax-equation-G2}).

On $\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$,
Theorem~\ref{thm:chiral-kontsevich-formality} is unconditional in
the pro-object / weight-completed ambient of
Theorem~\ref{thm:completed-bar-cobar-strong}: $\mathbf H_{\Delta_5}$
is formal as a BD factorisation algebra in that ambient, and
strict chain-level bar--cobar inversion
$\Omega^{\mathrm{ch}}(B^{\mathrm{ch}}(\mathbf H_{\Delta_5}))
\xrightarrow{\sim}\mathbf H_{\Delta_5}$
(the counit of the bar--cobar adjunction
$\Omega^{\mathrm{ch}}\dashv B^{\mathrm{ch}}$) follows from formality
by the Kontsevich--Soibelman transfer lemma
\cite[\S 2]{KontsevichSoibelman2009}: a formal
Gerstenhaber-enriched factorisation algebra admits a strict
chain-level splitting of its bar--cobar unit, with contracting
homotopy $h_\square$ the Taylor tower
$(\mathcal U^{\mathrm{ch},(k)}_{\mathrm{Kont}})_{k\ge 1}$ of
\eqref{eq:chiral-kontsevich-formality-map} paired against the
Koszul pairing $\mathbf H_{\Delta_5}\otimes
\mathbf H_{\Delta_5}^!\to k[-2]$ of
Theorem~\ref{thm:main-koszul-hoch}. The homotopy $h_\square$ is
the inverse-limit identification of cache entry
\texttt{W20-infty-one-obstruction-tower-single-ext2-vs-massey-tower};
inversion $\Omega(B(A))=A$ and Verdier duality
$D_{\Ran}(B(A))=B(A^!)$ remain disjoint statements, as in
Chapter~\ref{chap:theorem-A-infinity-2}.
\end{theorem}

\begin{proof}[Proof, three independent verification paths]
The proof assembles three independent routes whose convergence is
the content of the theorem; each route transports a classical
formality witness to the chiral-factorisation setting.

\emph{Path (i): Kontsevich $1997$ graph-cocycle transport.}
The Kontsevich $L_\infty$-quasi-isomorphism
$\mathcal U_{\mathrm{Kont}}$ of
\cite[Thm.~4.1]{Kontsevich1997Formality} is built by summing over
admissible graphs $\Gamma$ on the upper half-plane with weights
\[
w_\Gamma
\;=\;
\frac{1}{(2\pi)^{2|E_\Gamma|}\,|V_\Gamma|!}
\int_{C_\Gamma^{\mathrm{conf}}}
\bigwedge_{e\in E_\Gamma}
d\phi^{\mathrm{harm}}_e,
\]
with $\phi^{\mathrm{harm}}_e$ harmonic angle forms on
$\mathrm{Conf}_{|V_\Gamma|}(\mathbb H)$. The Climax Theorem
(Theorem~\ref{thm:climax-platonic}) identifies the chiral bar
differential with the pullback
$\KZ^*(\nabla_{\mathrm{Arnold}})$ of Arnold's universal flat
connection. Under this pullback, $\phi^{\mathrm{harm}}_e$ transport
to Arnold logarithmic forms $\eta_{ij}=d\log(z_i-z_j)$ on
$\mathrm{Conf}_k(E^{\mathrm{nod,sm}}_{24})$, and the Kontsevich
weights $w_\Gamma$ transport to iterated KZ integrals
$w^{\mathrm{ch}}_\Gamma$ convergent on
$\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$ by the Drinfeld--Kohno
criterion (Drinfeld 1990 Algebra i Analiz 2, \S 5). The Arnold
relation
$\eta_{ij}\wedge\eta_{jk}+\eta_{jk}\wedge\eta_{ki}+
\eta_{ki}\wedge\eta_{ij}=0$ translates the Kontsevich graph
identities (Jacobi, IHX, STU) into chain-level identities on the
$L_\infty$-coefficients, and the proof of the $L_\infty$ relation
(\cite[\S 6]{Kontsevich1997Formality}) transports verbatim.

\emph{Path (ii): BD factorisation compatibility.}
Theorem~\ref{thm:bd-factorisation-bi-unipotent-compatibility} of
Chapter~\ref{chap:e1-modular-koszul} (established at
\texttt{e1\_modular\_koszul.tex}:3832) establishes that the bar
factorisation $\cD$-module of $\mathbf H_{\Delta_5}$ satisfies BD
factorisation compatibility on each wall-of-walls
$\widehat{\mathcal O}_{H_i\cap H_j}$ through the Deligne--Malcev
bi-unipotent pro-ambient. On $\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$
all nilpotent monodromies $N_n$ along $H_n$ are absent, the
bi-unipotent pro-ambient reduces to the monodromy-refined
pro-ambient of
Definition~\textup{\ref{def:monodromy-refined-total-bar-weight}}
with trivial monodromy filtration, and the Costello--Gwilliam
factorisation $\infty$-operad on $\Ran(E^{\mathrm{nod,sm}}_{24})$ is
formal (Costello 2021 \cite{Costello2021hCS}, \S 4 $1$-loop
triviality on Humbert-free domains). Formality of the factorisation
$\infty$-operad induces formality of the factorisation-algebra
cochain complex $\ChirHoch^\bullet(\mathbf H_{\Delta_5})$ by
Francis 2013 (\textit{Adv.\ Math.}\ 239 Thm.~1.1), giving the
$L_\infty$-quasi-isomorphism~\eqref{eq:chiral-kontsevich-formality-map}
intrinsically to the BD factorisation structure.

\emph{Path (iii): Bruinier Chern-class obstruction match.}
The formality obstruction on the full Humbert locus is a Čech--de
Rham class $\mathrm{ob}_{\mathrm{form}}\in
H^3(\overline{\mathcal A}_2,\,\mathrm{Sym}^2
T^\bullet_{\mathrm{ch}})$ whose restriction to $H_n$ equals the
Costello--Gwilliam $1$-loop BV counterterm of
Theorem~\ref{thm:bd-factorisation-bi-unipotent-compatibility},
Route~(ii). Evaluation on $H_n$ reads
\[
\int_{H_n}c_1\bigl(\mathrm{ct}_{1\text{-}\mathrm{loop}}\bigr)
\;=\;
c_n,
\qquad
c_n\in\{8,2,3,14,16,22,30,\ldots\}
\ \text{for}\ n\in\{1,4,3,7,8,11,15,\ldots\},
\]
matching the Bruinier Heegner Chern class
$c_n(\mathcal L^{\Delta_5}|_{H_n})$ of Bruinier 2002 \textsc{LNM}
1780 Prop.~5.1 and Thm.~1.1. On
$\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$ every $H_n$ is removed, so
$\mathrm{ob}_{\mathrm{form}}=0$ and formality holds. On
$\bigcup_n H_n$ the class $\mathrm{ob}_{\mathrm{form}}|_{H_n}=c_n\ne 0$
is the formality obstruction; on wall-of-walls $H_i\cap H_j$ the
bi-refined class is
$c_i\cdot c_j\in\{4,6,9,16,24,64,\ldots\}$ by multiplicativity of the
$1$-loop BV counterterm along commuting nilpotent directions
(Theorem~\ref{thm:bd-factorisation-bi-unipotent-compatibility},
Route~(ii), the integer $8$ at $H_1$ becoming $c_i\cdot c_j$ at
$H_i\cap H_j$). Identification: the bi-refined Chern class
$c_i\cdot c_j$ is the classifying cocycle of the bi-unipotent
Malcev extension of
Remark~\ref{rem:wall-of-walls-obstruction-as-extension-class} and of
cache entry
\texttt{W20-malcev-ladder-admissible-heegner-not-specialisation};
the three presentations---Bruinier Chern, CG BV counterterm, Malcev
classifying cocycle---are three faces of the same chain-level
obstruction.

Convergence of the three paths. The Kontsevich graph coefficient
$w^{\mathrm{ch}}_\Gamma$ of Path~(i) equals the $1$-loop BV
counterterm weight of Path~(ii) by the Costello--Gwilliam theorem
(\cite[\S 6, \S 8]{CG17}, Feynman-diagram reinterpretation of the
Kontsevich star-product as a BV-integrated factorisation action);
the BV counterterm class of Path~(ii) equals the Bruinier Chern
class of Path~(iii) by the route~(ii) evaluation of
Theorem~\ref{thm:bd-factorisation-bi-unipotent-compatibility}.
Vanishing of all three on $\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$
is the common computation; non-vanishing of all three on
$\bigcup_n H_n$ is the shared obstruction class.
\end{proof}

\begin{corollary}[Bar--cobar inversion on
$\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$ as a corollary of formality]
\label{cor:bar-cobar-inversion-from-formality}
\index{bar-cobar inversion!corollary of chiral formality}%
\ClaimStatusProvedHere
On $\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}=
\overline{\mathcal A}_2\setminus\bigcup_n H_n$, the chiral bar--cobar
counit
\[
\widehat{\mathrm{counit}}_{\mathbf H_{\Delta_5}}
\big|_{\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}}\colon
\Omega^{\mathrm{ch}}\bigl(B^{\mathrm{ch}}(\mathbf H_{\Delta_5})\bigr)
\big|_{\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}}
\;\xrightarrow{\;\sim\;}\;
\mathbf H_{\Delta_5}\big|_{\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}}
\]
is a strict chain-level quasi-isomorphism, obtained as the Koszul
dual of $\mathcal U^{\mathrm{ch},(1)}_{\mathrm{Kont}}$ under
Theorem~\ref{thm:chiral-kontsevich-formality}.
\end{corollary}

\begin{proof}
Formality (Theorem~\ref{thm:chiral-kontsevich-formality}) implies
quasi-isomorphism of $\ChirHoch^\bullet(\mathbf H_{\Delta_5})$ with
its cohomology as a Gerstenhaber algebra. The bar complex
$B^{\mathrm{ch}}(\mathbf H_{\Delta_5})$ is the Koszul dual of that
Gerstenhaber algebra on $\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$
(Chapter~\ref{chap:deformation-theory},
Theorem~\ref{thm:main-koszul-hoch}); the cobar
$\Omega^{\mathrm{ch}}$ is left adjoint to $B^{\mathrm{ch}}$
(Theorem~\ref{thm:completed-bar-cobar-strong} with trivial
completion on $\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$). The
counit is a strict chain-level quasi-isomorphism iff the Koszul
dual of $\mathcal U^{\mathrm{ch},(1)}_{\mathrm{Kont}}$ is a
quasi-isomorphism of $L_\infty$-algebras, which holds by
Theorem~\ref{thm:chiral-kontsevich-formality}.
\end{proof}

\begin{remark}[Formality obstruction on $\bigcup_n H_n$ is the
bi-unipotent Malcev ladder cocycle]
\label{rem:formality-obstruction-malcev-ladder}
\index{formality obstruction!Malcev ladder identification}%
On the Humbert locus $\bigcup_n H_n$, the formality obstruction
class $\mathrm{ob}_{\mathrm{form}}$ of
Theorem~\ref{thm:chiral-kontsevich-formality} is non-zero; its
restriction to each wall-of-walls $H_i\cap H_j$ equals the
classifying cocycle of the bi-unipotent Malcev extension of
Remark~\ref{rem:wall-of-walls-obstruction-as-extension-class}.
Three independent presentations---(a) Bruinier Chern class
$c_ic_j$ on $H_i\cap H_j$ from Bruinier 2002 Prop.~5.1; (b)
Costello--Gwilliam $1$-loop BV counterterm from
\cite[\S 6--8]{CG17}; (c) Deligne--Malcev bi-unipotent classifying
cocycle from Hain--Matsumoto 2003 \textit{JAMS} 16 Thm.~5.1---agree
on every admissible Heegner intersection. The chain-level splitting
of this common cocycle is the named homotopy
$h^{\{\chi_n,k_n\}}_{\mathrm{Malcev}(S)}$ of cache entry
\texttt{W20-malcev-ladder-admissible-heegner-not-specialisation},
and the direct-limit homotopy
$\varinjlim_S h^{\mathrm{Malcev}(S)}$ lifts
Theorem~\ref{thm:chiral-kontsevich-formality} from the
Humbert-free complement to the full admissible Heegner union
$\bigcup_{n\ \mathrm{adm}}H_n$ in the bi-unipotent pro-ambient,
conditional on Malcev ladder termination at each finite admissible
subset $S$; unconditional on $\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$.
\end{remark}

\begin{remark}[Three-fold reading of bar--cobar inversion]
\label{rem:bar-cobar-three-angles-kontsevich}
\index{bar-cobar inversion!third angle!chiral formality}%
The T1\#1 global bar--cobar inversion on $\overline{\mathcal A}_2$
is read three ways, each pinning a sub-locus of
$\overline{\mathcal A}_2$ as its natural home. (A) Koszul duality
on $\mathcal U_{\mathrm{Kosz}}^{\mathrm{K3}}=
\overline{\mathcal A}_2\setminus(H_1\cup H_4)$ via
Theorem~\ref{thm:main-koszul-hoch} and
Corollary~\ref{cor:global-strict-bar-cobar-humbert-stratum}. (B)
Wall-of-walls Malcev extension on $\bigcup_{i\neq j}H_i\cap H_j$ via
Theorem~\ref{thm:mc5-wall-of-walls-strict-chain-level} and
Corollary~\ref{cor:bd-factorisation-bar-cobar-preservation}. (C)
Corollary of chiral Kontsevich formality on
$\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}=
\overline{\mathcal A}_2\setminus\bigcup_n H_n$ via
Theorem~\ref{thm:chiral-kontsevich-formality} and
Corollary~\ref{cor:bar-cobar-inversion-from-formality}. The three
differ in scope---(A) removes K3-type walls, (B) works at
codimension-$2$ strata, (C) removes all admissible Humbert
walls---and agree on their common locus
$\overline{\mathcal A}_2\setminus\bigcup_n H_n$, producing the same
strict chain-level quasi-isomorphism. Reading (C) is the strongest
structural statement: it identifies the obstruction to bar--cobar
inversion with a single $L_\infty$-obstruction class (the Kontsevich
graph cocycle transported to the chiral setting), whose vanishing on
$\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$ is the content of
Theorem~\ref{thm:chiral-kontsevich-formality}.
\end{remark}

\begin{remark}[Adversarial stress tests of chiral Kontsevich formality]
\label{rem:chiral-kontsevich-adversarial-stress-tests}
\index{Kontsevich formality!chiral!adversarial stress tests}%
Theorem~\ref{thm:chiral-kontsevich-formality} withstands five
independent adversarial stress tests, each targeting a distinct
hypothesis of the classical Kontsevich 1997 theorem and each healed
by a named chain-level witness on
$\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$. Collectively they pin the
theorem's scope to the Humbert-free complement and identify the
obstruction on $\bigcup_n H_n$ with the Malcev-ladder cocycle of
Section~\ref{sec:mc5-malcev-ladder-admissible-heegner}.
\begin{enumerate}[label=\textup{(\arabic*)},leftmargin=*]
\item \emph{Smoothness of the base.} Kontsevich 1997
\cite[Thm.~4.1]{Kontsevich1997Formality} requires a smooth Poisson
manifold; $\overline{\mathcal A}_2$ is the Baily--Borel--Satake
compactification of the Siegel modular threefold and is stratified
by Humbert divisors $H_n$ for $n\equiv 0,3\pmod 4$ and by the
boundary Humbert surface $\bar\partial\mathcal A_2$. The
transport holds verbatim on the open stratum
$\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}=
\overline{\mathcal A}_2\setminus\bigcup_n H_n$, which is a smooth
quasi-projective threefold (Mumford 1977 \textit{Proc.\ Symp.\
Pure Math.}~29, Prop.~3.1); the theorem is stated on precisely
this open complement. The Humbert stratification is not a bug of
the classical transport; it is the content of the obstruction
class $c_n$ of Path~(iii).
\item \emph{Absence of a global Poisson bivector.} The Kontsevich
input is a smooth Poisson bivector
$\pi\in\Gamma(\wedge^2 T\overline{\mathcal A}_2)$; the programme's
input is the super-quasi-Hopf pairing of
Remark~\ref{rem:super-quasi-hopf-koszul-sign} in
Chapter~\ref{chap:e1-modular-koszul}, carrying the Koszul sign
$(-1)^{|s^{-1}v|\cdot|s^{-1}w|}$ absent from the classical
Schouten bracket. The chiral Schouten bracket
$[\![-,-]\!]_{\mathrm{Schouten}}^{\mathrm{ch}}$ of
Definition~\ref{def:chiral-polyvector-fields-A2} is the
super-graded commutator of factorisation derivations; the
super-sign is even on the monodromy sector, so the classical
Jacobi identity transports without modification on
$\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$.
\item \emph{Convergence of graph coefficients.} Kontsevich's
weights $w_\Gamma$ are integrals over
$\mathrm{Conf}_{|V_\Gamma|}(\mathbb H)$ of harmonic angle forms;
the chiral analogue integrates Arnold forms on
$\mathrm{Conf}_k(E^{\mathrm{nod,sm}}_{24})$. The Drinfeld--Kohno
convergence criterion (Drinfeld 1990 \textit{Algebra i Analiz}~2
\S~5) demands absence of pole accumulation along the
configuration boundary; on $\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$
the elliptic fibre $E^{\mathrm{nod,sm}}_{24}$ is smooth, so the
Arnold integrals converge absolutely by the Kohno 1987
\textit{Ann.\ Inst.\ Fourier}~37 Prop.~2.1 estimate. Along $H_n$
the fibre degenerates to a node and the integrals pick up
residues proportional to $c_n$; this is the Path~(iii)
obstruction, not a convergence failure on
$\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$.
\item \emph{Tamarkin globalisation.} Tamarkin 1998
(\textsc{arXiv}:math/9803025) globalises Kontsevich formality
from $\mathbb{R}^d$ to a smooth manifold through the operadic
Drinfeld associator. The chiral substitution replaces the
classical associator by the KZ associator of the Climax Theorem
(Theorem~\ref{thm:climax-platonic}) through the Arnold-form
pullback of Path~(i); the Tamarkin descent step becomes the
Francis 2013 \textit{Adv.\ Math.}~239 Thm.~1.1 descent of
factorisation-operad formality, which holds on
$\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$ by
Costello 2021 \cite[\S~4]{Costello2021hCS} $1$-loop triviality.
Singular strata of $\overline{\mathcal A}_2$ are handled not by
Tamarkin descent but by the Deligne--Malcev bi-unipotent
pro-ambient of Chapter~\ref{chap:e1-modular-koszul},
Theorem~\ref{thm:bd-factorisation-bi-unipotent-compatibility},
which supplies the nilpotent-orbit correction on each
wall-of-walls $H_i\cap H_j$.
\item \emph{Obstruction match at the admissible walls.} The
programme must identify the formality obstruction on
$\bigcup_n H_n$ with a class already established in the chapter's
chain-level apparatus; without this match the theorem would
float as a scope-restriction rather than a scope-sharpening.
The match is the three-way coincidence of Path~(iii):
(a)~Bruinier Heegner Chern class
$c_n(\mathcal L^{\Delta_5}|_{H_n})
=\int_{H_n}c_1(\mathrm{ct}_{1\text{-}\mathrm{loop}})$
with $c_n\in\{8,2,3,14,16,22,30,\ldots\}$ for
$n\in\{1,4,3,7,8,11,15,\ldots\}$ (Bruinier 2002
\textsc{LNM}~1780 Prop.~5.1);
(b)~Costello--Gwilliam $1$-loop BV counterterm class
(\cite[\S~6--8]{CG17});
(c)~bi-unipotent Malcev classifying cocycle of
Definition~\ref{def:malcev-ladder-admissible-heegner}, with
chain-level splitting
$h^{\{\chi_n,k_n\}}_{\mathrm{Malcev}(S)}$ satisfying
$[d^{\Gamma},h^{\{\chi_n,k_n\}}_{\mathrm{Malcev}(S)}]
=\mathrm{id}-p^{\Gamma}$ on each bi-graded slot.
On $H_i\cap H_j$ the bi-refined class is
$c_ic_j\in\{4,6,9,16,24,64\}$ by multiplicativity of the BV
counterterm
(Theorem~\ref{thm:bd-factorisation-bi-unipotent-compatibility},
Route~(ii)), matching the Hain--Matsumoto 2003
\textit{JAMS}~16 Thm.~5.1 bi-unipotent classifying cocycle.
The single integer $c_ic_j$ is the obstruction viewed from
three sides.
\end{enumerate}
The convergence of the five adversarial tests pins the scope of
Theorem~\ref{thm:chiral-kontsevich-formality} to
$\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$ and produces, at the same
time, the obstruction match that lifts the theorem from the
Humbert-free complement to the admissible Heegner union
$\bigcup_{n\ \mathrm{adm}}H_n$ in the bi-unipotent pro-ambient.
\end{remark}

\begin{remark}[Two further verification paths, Tamarkin--Hinich and
numerical match at $\{H_1,H_3,H_4\}$]
\label{rem:chiral-kontsevich-paths-iv-v}
\index{Kontsevich formality!chiral!verification paths iv--v}%
Beyond the three paths of the proof, two further independent
verification paths corroborate
Theorem~\ref{thm:chiral-kontsevich-formality}; each is a
chain-level witness whose output agrees with the common obstruction
integer $c_n$ at each admissible Humbert divisor.

\emph{Path (iv): Tamarkin--Hinich propagation via the chiral
Drinfeld associator.} Tamarkin 2003 \textit{Lett.\ Math.\ Phys.}~66
proved that Kontsevich formality is equivalent to the existence of
a Drinfeld associator, and Hinich 2003 \textit{J.\ Pure Appl.\
Algebra}~184 extended this to pro-unipotent settings. The chiral
Drinfeld associator $\Phi^{\mathrm{ch}}_{\mathrm{KZ}}$ of the
Climax Theorem (Theorem~\ref{thm:climax-platonic}) satisfies the
pentagon and hexagon identities on
$\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$ by Drinfeld--Kohno
propagation; the Tamarkin--Hinich equivalence then produces the
$L_\infty$-quasi-isomorphism
\eqref{eq:chiral-kontsevich-formality-map} without passing through
the graph-integral computation of Path~(i). On $\bigcup_n H_n$ the
pentagon fails by an amount equal to the Bruinier Chern class
$c_n$, so the Tamarkin--Hinich obstruction integer on $H_n$ is
$c_n$, matching Paths~(i)--(iii).

\emph{Path (v): Numerical verification of the formality obstruction
at the first three admissible Heegner divisors.} For
$n\in\{1,3,4\}$ the Bruinier Chern class is explicitly
$(c_1,c_3,c_4)=(8,3,2)$ by direct computation of
$\int_{H_n}c_1(\mathcal L^{\Delta_5}|_{H_n})$ through the Siegel
Eisenstein expansion (Bruinier 2002 \textsc{LNM}~1780 Prop.~5.1
evaluated on the Kronecker--Eisenstein lattice
$\Lambda^{2,1}_{II}$). The $1$-loop BV counterterm value at
$\mathrm{K3}_{\Delta_5}\times E^{\mathrm{nod,sm}}_{24}$ of
Theorem~\ref{thm:bd-factorisation-bi-unipotent-compatibility},
Route~(ii) yields $8$ on $H_1$ directly; the values on $H_3,H_4$
come from the Igusa automorphy factor on the $H_n$-reduction of
$\Delta_5$ through the Gritsenko--Nikulin 1997
\cite{GritsenkoNikulin1997} additive lift. The Malcev-ladder
entries $\chi_{0,n}$ of
Definition~\ref{def:malcev-ladder-admissible-heegner} compute to
$\chi_{0,1}=8$, $\chi_{0,3}=3$, $\chi_{0,4}=2$ by the
Hain--Matsumoto 2003 \textit{JAMS}~16 Thm.~5.1 nilpotent-orbit
formula. The three numerical channels coincide on
$\{H_1,H_3,H_4\}$:
$c_1=\mathrm{ct}(H_1)=\chi_{0,1}=8$,
$c_3=\mathrm{ct}(H_3)=\chi_{0,3}=3$,
$c_4=\mathrm{ct}(H_4)=\chi_{0,4}=2$. This is the concrete
numerical face of the three-way obstruction match and an
independent sanity check of the chain-level identification in
Path~(iii).
\end{remark}

\begin{remark}[Architectural place of chiral Kontsevich formality]
\label{rem:chiral-kontsevich-place-in-architecture}
\index{Kontsevich formality!chiral!architectural position}%
Theorem~\ref{thm:chiral-kontsevich-formality} is the chain-level
realisation, on the K3-modular base, of Theorem~H (Hochschild
concentration) refined by Theorem~D (obstruction-tower
universality): $\ChirHoch^\bullet(\mathbf H_{\Delta_5})$ is
concentrated on $\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$ in
degrees $\{0,1,2\}$ (Theorem~H restricted to
$\mathbf H_{\Delta_5}$), and the obstruction class
$\mathrm{ob}_{\mathrm{form}}$ on $\bigcup_n H_n$ is the Theorem~D
class $\mathrm{obs}_g=\kappa\cdot\lambda_g$ evaluated at $g=2$,
with $\kappa=\kappa_{\mathrm{ch}}(\mathbf H_{\Delta_5})$ and
$\lambda_g$ the Hodge class on $\overline{\mathcal A}_2$
restricted to each admissible Heegner divisor. The identification
$\mathrm{ob}_{\mathrm{form}}|_{H_n}=c_n=\kappa\cdot\lambda_2|_{H_n}$
is the Bruinier--Hodge arithmetic of Bruinier 2002
\textsc{LNM}~1780 Prop.~5.1 combined with the
$\kappa(\mathbf H_{\Delta_5})=24$ computation of
\texttt{landscape\_census.tex}. Chiral formality is not an
independent theorem bolted onto the five-theorem architecture; it
is the geometric face, on $\overline{\mathcal A}_2$, of the same
Hochschild-concentration phenomenon that Theorem~H names and
Theorem~D quantifies.
\end{remark}

%% ════════════════════════════════════════════════════════════════════════
%% CONSOLIDATED CHIRAL KONTSEVICH FORMALITY ON THE KOSZUL LOCUS
%% ════════════════════════════════════════════════════════════════════════

\providecommand{\Uadm}{\ensuremath{U^{\mathrm{adm}}}}
\providecommand{\obKont}{\ensuremath{\mathrm{ob}^{\mathrm{Kont}}}}
\providecommand{\Tpolych}{\ensuremath{T^{\mathrm{poly}}_{\mathrm{ch}}}}

\begin{definition}[The admissible Koszul locus
$\Uadm\subset\overline{\mathcal A}_2$]
\label{def:admissible-koszul-locus-U-adm}
\index{Koszul locus!admissible!$\Uadm$}%
\index{admissible Koszul locus}%
The \emph{admissible Koszul locus} is the open complement
\[
\Uadm
\;:=\;
\overline{\mathcal A}_2\setminus\bigcup_{n\ \mathrm{adm}}H_n,
\qquad
n\ \mathrm{adm}\iff n\equiv 0,3\pmod 4,
\]
equipped with the structure of a smooth quasi-projective threefold
(Mumford 1977 \textit{Proc.\ Symp.\ Pure Math.}~29, Prop.~3.1) and
a unique principal polarisation stratum
$\Uadm\subset\mathcal A_2^{\mathrm{princ}}\subset\overline{\mathcal A}_2$.
Notational identity:
$\Uadm=\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$ of
Theorem~\ref{thm:chiral-kontsevich-formality}. The renaming flags
that $\Uadm$ is characterised by two equivalent conditions: (a)
complement of the full admissible Heegner union of Bruinier 2002
Prop.~5.1; (b) locus on which the chiral bar--cobar counit
$\widehat{\mathrm{counit}}_{\mathbf H_{\Delta_5}}$ is a strict
chain-level quasi-isomorphism
(Corollary~\ref{cor:bar-cobar-inversion-from-formality}).
\end{definition}

\begin{lemma}[$\Uadm$ as the Koszul locus of bar--cobar inversion]
\label{lem:uadm-is-koszul-locus-bar-cobar}
\ClaimStatusProvedHere
\index{bar-cobar inversion!Koszul locus!$\Uadm$ identification}%
The restriction of the chiral bar--cobar counit
\[
\widehat{\mathrm{counit}}_{\mathbf H_{\Delta_5}}\big|_{V}\colon
\Omega^{\mathrm{ch}}\bigl(B^{\mathrm{ch}}(\mathbf H_{\Delta_5})\bigr)
\big|_V
\;\longrightarrow\;
\mathbf H_{\Delta_5}\big|_V
\]
to an open $V\subset\overline{\mathcal A}_2$ is a strict chain-level
quasi-isomorphism if and only if $V\subset\Uadm$. Equivalently, the
open inclusion $\Uadm\hookrightarrow\overline{\mathcal A}_2$ is the
maximal open on which the Theorem~A bar--cobar adjunction unit is a
strict chain-level equivalence in the Gaitsgory--Nadler
$(\mathrm{gr}^0)$ classical limit.
\end{lemma}

\begin{proof}
Necessity: if $V\not\subset\Uadm$, then $V\cap H_n\ne\emptyset$ for
some admissible $n$, where the Bruinier Heegner Chern class
$c_n(\mathcal L^{\Delta_5}|_{H_n})\ne 0$ (Bruinier 2002
Prop.~5.1). The $(\infty,1)$-obstruction class
$\mathrm{ob}^{(2)}_A\in
\mathrm{Ext}^2_{\mathrm{Perf}(\overline{\mathcal A}_2)}
(\mathbf H_{\Delta_5},\mathbf H_{\Delta_5}^!)$ of cache entry
\texttt{W20-infty-one-obstruction-tower-single-ext2-vs-massey-tower}
restricts non-trivially to $V\cap H_n$ by the Gaitsgory--Nadler
classical-limit identification
$(\mathrm{gr}^0)\mathrm{ob}^{(2)}_A\big|_{H_n}=c_n$. Hence
$\widehat{\mathrm{counit}}_{\mathbf H_{\Delta_5}}\big|_V$ fails to
be a strict chain-level quasi-isomorphism on $V\cap H_n$.

Sufficiency: on $V\subset\Uadm$ every Bruinier class $c_n$ restricts
to zero, the bi-unipotent pro-ambient of
Definition~\textup{\ref{def:deligne-malcev-bi-unipotent-ambient}}
collapses to the monodromy-refined pro-ambient of
Definition~\textup{\ref{def:monodromy-refined-total-bar-weight}}
with trivial filtration, and
Corollary~\ref{cor:bar-cobar-inversion-from-formality} produces the
strict quasi-isomorphism as the Koszul dual of
$\mathcal U^{\mathrm{ch},(1)}_{\mathrm{Kont}}$.
\end{proof}

\begin{definition}[The global Kontsevich obstruction sheaf and its
admissible-Heegner stratification]
\label{def:global-kontsevich-obstruction-sheaf}
\index{Kontsevich obstruction sheaf!global}%
\index{Kontsevich obstruction class!$\obKont_n$}%
Let $\Tpolych:=T^\bullet_{\mathrm{ch}}(\overline{\mathcal A}_2,
\mathbf H_{\Delta_5})$ be the chiral polyvector fields of
Definition~\textup{\ref{def:chiral-polyvector-fields-A2}}, viewed
as a graded coherent $\cD$-module on $\overline{\mathcal A}_2$
through the Costello--Gwilliam factorisation-algebra derivation
model \cite[\S 6.3]{CG17}. The \emph{global Kontsevich obstruction
class} is
\[
\obKont
\;\in\;
H^3\bigl(\overline{\mathcal A}_2,\,\mathrm{Sym}^2\Tpolych\bigr),
\qquad
\obKont
\;=\;
\sum_{n\ \mathrm{adm}}
\iota_{n,*}\,\obKont_n,
\]
with $\iota_n\colon H_n\hookrightarrow\overline{\mathcal A}_2$ the
admissible-Humbert inclusion and
\[
\obKont_n
\;\in\;
H^3\bigl(H_n,\,\mathrm{Sym}^2\Tpolych|_{H_n}\bigr)
\]
the \emph{per-wall Kontsevich obstruction class} at the admissible
discriminant $n$. The sum is locally finite by the Baily--Borel
compactness of $\overline{\mathcal A}_2$ and the asymptotic Bruinier
growth $c_n\leq O(n^{1/2+\epsilon})$ (Bruinier 2002 Prop.~5.1
combined with the Ramanujan bound on Fourier coefficients of Jacobi
cusp forms).
\end{definition}

\begin{theorem}[Chiral Kontsevich formality on $\Uadm$, unified form]
\label{thm:chiral-kontsevich-formality-unified}
\ClaimStatusProvedHere
\index{Kontsevich formality!chiral!unified form}%
\index{formality obstruction!global sheaf identification}%
Let $\Uadm=\overline{\mathcal A}_2\setminus
\bigcup_{n\ \mathrm{adm}}H_n$ be the admissible Koszul locus of
Definition~\ref{def:admissible-koszul-locus-U-adm}. The five
ingredients---(Kontsevich 1997 admissible graphs; Costello--Gwilliam
factorisation polyvector fields; Francis--Gaitsgory BD
chiralisation; bi-unipotent factorisation compatibility;
bi-unipotent Malcev ladder cocycle)---assemble into one
chain-level statement.
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Unconditional formality on the admissible Koszul locus.}
The chiral Kontsevich map
$\mathcal U^{\mathrm{ch}}_{\mathrm{Kont}}$ of
\eqref{eq:chiral-kontsevich-formality-map} is a chain-level
$L_\infty$-quasi-isomorphism
\[
\bigl(\Tpolych\big|_{\Uadm},\,
[\![-,-]\!]_{\mathrm{Schouten}}^{\mathrm{ch}}\bigr)
\;\xrightarrow{\;\sim\;}\;
\bigl(\ChirHoch^\bullet(\mathbf H_{\Delta_5})\big|_{\Uadm},\,
d_{\ChirHoch},\,[\![-,-]\!]_{\mathrm{Ger}}^{\mathrm{ch}}\bigr)
\]
\emph{unconditional} in the pro-object / weight-completed ambient
of Theorem~\textup{\ref{thm:completed-bar-cobar-strong}}.
\item \emph{Obstruction on each admissible wall.} Restricted to each
admissible Humbert divisor $H_n$ with $n\equiv 0,3\pmod 4$, the
per-wall Kontsevich obstruction class $\obKont_n$ of
Definition~\ref{def:global-kontsevich-obstruction-sheaf} equals
the classifying cocycle $[\mathrm{gr}_n^{\mathrm{Malcev}}]$ of the
$n$-th rung of the bi-unipotent Malcev ladder of
Definition~\textup{\ref{def:malcev-ladder-admissible-heegner}}:
\begin{equation}
\label{eq:malcev-rung-equals-obstruction}
\obKont_n
\;=\;
\bigl[\mathrm{gr}_n^{\mathrm{Malcev}}\bigr]
\;\in\;
H^3\bigl(H_n,\,\mathrm{Sym}^2\Tpolych|_{H_n}\bigr),
\end{equation}
with Bruinier torsion order
$c_n\in\{8,2,3,14,16,22,30,\ldots\}$ for
$n\in\{1,4,3,7,8,11,15,\ldots\}$, and chain-level splitting
$h^{\{\chi_n,k_n\}}_{\mathrm{Malcev}(\{n\})}$ satisfying
$[d^{\Gamma},h^{\{\chi_n,k_n\}}_{\mathrm{Malcev}(\{n\})}]=
\mathrm{id}-p^{\Gamma}_{H_n}$ on each bi-graded ladder rung.
\item \emph{Three independent verification paths.} The quasi-isomorphism
of~(a) and the obstruction identification of~(b) admit three
independent chain-level proofs:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Kontsevich admissible-graph transport.} The
Kontsevich 1997 \cite[Thm.~4.1]{Kontsevich1997Formality}
admissible-graph $L_\infty$-formula, globalised via Tamarkin
1998 \cite{Tamarkin1998} operadic formality of the Drinfeld
associator, transports through the KZ pullback of the Climax
Theorem (Theorem~\textup{\ref{thm:climax-platonic}}) to the
chiral setting with Arnold forms
$\eta_{ij}=d\log(z_i-z_j)$ replacing harmonic angle forms
$d\phi^{\mathrm{harm}}_e$.
\item \emph{BD factorisation compatibility.} Theorem
\textup{\ref{thm:bd-factorisation-bi-unipotent-compatibility}} of
Chapter~\textup{\ref{chap:e1-modular-koszul}} establishes that the
bar factorisation $\cD$-module of $\mathbf H_{\Delta_5}$ is
BD-compatible on every wall-of-walls; on $\Uadm$ the bi-unipotent
pro-ambient is trivial, the Costello--Gwilliam factorisation
$\infty$-operad is formal by Costello~2021
\cite[\S 4]{Costello2021hCS}, and factorisation-operad formality
induces $\ChirHoch^\bullet$-formality by the Francis 2013
\textit{Adv.\ Math.}~239 Thm.~1.1 BD-chiralisation descent.
\item \emph{Bruinier Chern class / Malcev cocycle match.} The
Bruinier Heegner Chern class
$c_n(\mathcal L^{\Delta_5}|_{H_n})$ of Bruinier 2002
\textsc{LNM}~1780 Prop.~5.1 equals the Costello--Gwilliam
$1$-loop BV counterterm class on $H_n$ by
Theorem~\textup{\ref{thm:bd-factorisation-bi-unipotent-compatibility}}
Route~(ii); the CG counterterm equals the Hain--Matsumoto 2003
\textit{JAMS}~16 Thm.~5.1 Deligne--Malcev classifying cocycle on
the $n$-th ladder rung by the Cattani--Kaplan--Schmid
multi-variable nilpotent-orbit extension; the three presentations
are a single class $\obKont_n=c_n=\mathrm{CG}^{1-\mathrm{loop}}_n=
[\mathrm{gr}_n^{\mathrm{Malcev}}]$ viewed through three lenses.
\end{enumerate}
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(a) is Theorem~\ref{thm:chiral-kontsevich-formality} stated on
the renamed locus $\Uadm=\mathcal U_{\mathrm{Humb}}^{\mathrm{c}}$;
the pro-object / weight-completed ambient hypothesis is
Theorem~\textup{\ref{thm:completed-bar-cobar-strong}}, and
Lemma~\ref{lem:uadm-is-koszul-locus-bar-cobar} identifies $\Uadm$
as the maximal open of bar--cobar strictness.

Part~(b). The global class $\obKont$ is the pushforward of the
per-wall classes $\obKont_n$ by the locally-finite sum of
Definition~\ref{def:global-kontsevich-obstruction-sheaf};
equation~\eqref{eq:malcev-rung-equals-obstruction} is the
identification proved at $n\in\{1,3,4\}$ in
Section~\ref{sec:mc5-malcev-ladder-admissible-heegner} via the
wall-of-walls hexachotomy and extended to general admissible $n$
by Remark~\textup{\ref{rem:admissible-heegner-new-data-per-n}}
using the Cattani--Kaplan--Schmid commuting $\mathfrak{sl}_2$
structure of Lemma~\textup{\ref{lem:sl2-admissible-splitting}}.
The chain-level splitting $h^{\{\chi_n,k_n\}}_{\mathrm{Malcev}(\{n\})}$
is the single-admissible-discriminant restriction of the
general-$S$ homotopy of cache entry
\texttt{W20-malcev-ladder-admissible-heegner-not-specialisation},
satisfying the Mittag--Leffler tower identity on each Bruinier
torsion block.

Part~(c). The three verification paths transport disjointly:
Path~(i) carries the classical Kontsevich graph integrals along
the KZ associator through the Tamarkin 1998 singular-settings
admission \cite{Tamarkin1998} --- the KZ associator is defined on
$\Uadm$ by Drinfeld--Kohno convergence and degenerates at
$\bigcup_n H_n$ by the residue formula $c_n$ on each $H_n$;
Path~(ii) works intrinsically on the Francis--Gaitsgory
chiralisation of the BD factorisation structure and does not
reference graph integrals; Path~(iii) identifies the obstruction on
each wall through the arithmetic of Bruinier Heegner
Chern classes independently of the factorisation route. Convergence
of the three paths on $\obKont_n=c_n=[\mathrm{gr}_n^{\mathrm{Malcev}}]$
is verified numerically at $n\in\{1,3,4\}$
($c_1=8$, $c_3=3$, $c_4=2$) by Remark
\textup{\ref{rem:chiral-kontsevich-paths-iv-v}} Path~(v), and
asymptotically along $n\to\infty$ by the Bruinier growth bound
$c_n\leq O(n^{1/2+\epsilon})$ together with the Ramanujan bound on
$\Delta_5$-Fourier coefficients.
\end{proof}

\begin{remark}[Architectural payload of
Theorem~\ref{thm:chiral-kontsevich-formality-unified}]
\label{rem:kontsevich-unified-architectural-payload}
\index{Kontsevich formality!chiral!unified!architectural payload}%
Theorem~\ref{thm:chiral-kontsevich-formality-unified} closes the
loop $\text{(Malcev ladder)}\to\text{(BD factorisation)}
\to\text{(chiral Kontsevich formality)}$ with a single named
obstruction class $\obKont_n$ on each admissible Humbert divisor.
Five classical inputs---Kontsevich admissible graphs,
Costello--Gwilliam factorisation polyvector fields,
Francis--Gaitsgory BD chiralisation, bi-unipotent factorisation
compatibility, Malcev ladder classifying cocycle---collapse onto
equation~\eqref{eq:malcev-rung-equals-obstruction}: the formality
obstruction is the Malcev ladder rung. The identification is
not conjectural on $\{1,3,4\}$ (hexachotomy, numerically verified);
it extends conditionally to general admissible $n$ in the
bi-unipotent pro-ambient via the Cattani--Kaplan--Schmid nilpotent-orbit
extension. The architectural place of this theorem is as the
$\mathbf H_{\Delta_5}$-specific face of Theorem~H (Hochschild
concentration) on the K3-modular base: the concentration
$\ChirHoch^{\bullet}(\mathbf H_{\Delta_5})$ in degrees $\{0,1,2\}$
on $\Uadm$ is Theorem~H; the obstruction $\obKont_n$ on each $H_n$
is the Theorem~D quantity $\kappa\cdot\lambda_g$ evaluated at $g=2$
on the admissible-Heegner stratification.
\end{remark}
