%% Motivic Shadow Tower Extension to the Full Class M -- Platonic Chapter.
%%
%% Companion chapter to chapters/theory/motivic_shadow_tower.tex, which
%% established motivic rationality of the Virasoro shadow tower
%% (thm:virasoro-motivic-rationality-all-r). The present chapter extends
%% the motivic MZV-freeness to the complete class M:
%%
%%   (1) W_N principal for all N >= 2 at generic central charge c
%%       (all r >= 2, every generator line W_j for 2 <= j <= N;
%%        each line's Riccati sub-tower reduces to the Virasoro case
%%        by the depth-1 theorem plus Fateev-Lukyanov OPE rationality);
%%   (2) Bershadsky-Polyakov in Arakawa convention (all r >= 2);
%%   (3) W_infinity at generic Psi (all r >= 2, T-line);
%%   (4) Tempered Virasoro (remark: not independently realized);
%%
%% and proves the STRUCTURAL reason: shadow-tower residues on Conf_n(D)
%% extract depth-1 Arnold data only, hence Q(c)-rational outputs. The
%% E_2-topological Drinfeld associator, by contrast, carries depth-2 MZV
%% via iterated Arnold integrals; this is the sharp E_1-chiral vs
%% E_2-topological distinction (thm:e1-vs-e2-mzv-depth-distinction).
%%
%% ARCHITECTURE. Six self-contained inscriptions:
%%
%%   Section 1. Structural theorem: shadow residues are depth-1 data.
%%     (thm:shadow-tower-depth-1-rationality,
%%      thm:e1-vs-e2-mzv-depth-distinction)
%%
%%   Section 2. W_N principal rationality for all r, all lines.
%%     (thm:w-n-motivic-rationality-all-r,
%%      prop:w3-w-line-motivic-rationality)
%%
%%   Section 3. Bershadsky-Polyakov rationality (Arakawa convention).
%%     (thm:bp-motivic-rationality-arakawa,
%%      prop:bp-fl-convention-caveat)
%%
%%   Section 4. W_infinity rationality at generic Psi.
%%     (thm:w-infty-motivic-rationality-all-r)
%%
%%   Section 5. Full class M summary theorem.
%%     (thm:class-m-motivic-rationality-full)
%%
%%   Section 6. Tempered Virasoro remark and frontier.
%%     (rem:tempered-virasoro-not-realized)
%%
%% No AI attribution. All work attributed to Raeez Lorgat.

\chapter{Motivic rationality of the full class-M shadow tower}
\label{ch:motivic-class-m-full}

\begin{overture}
The Virasoro shadow tower is motivic-rational
(Theorem~\ref{thm:virasoro-motivic-rationality-all-r}); no
$\zet^{\mot}$ enters at any weight. This is surprising only if one
expects the $\MZV^{\mot}$-content of the Kontsevich--Drinfeld
formality (which populates the Drinfeld associator $\Phi_{\KZ}$) to
propagate into the shadow tower via the $E_2$-structure on the
derived centre. It does not propagate, and the obstruction is
structural: the shadow tower lives on the $E_1$-chiral bar side, not
on the $E_2$-coproduct side. We prove this obstruction is
\emph{depth-1 pure} for every chirally Koszul algebra
(Theorem~\ref{thm:shadow-tower-depth-1-rationality}), and extract the
consequence: rationality lifts from Virasoro to the full class M:
principal $\cW_N$ for all $N \geq 2$, Bershadsky--Polyakov, and
$\cW_{\infty}$ at generic Miura parameter $\Psi$.
\end{overture}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Depth-1 rationality of the shadow-tower residue}
\label{sec:depth-1-rationality}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The shadow coefficient $S_r(\cA)$ is extracted from the universal
Maurer--Cartan element $\Theta_{\cA}$ on the bar complex
$B^{\ord}(\cA) = T^c(s^{-1} \bar{\cA})$ on $\mathrm{Conf}_n(D)$. It is
a functional of OPE residues (depth-$1$ Arnold data), not of iterated
Arnold integrals (depth-$\geq 2$ MZV data). We prove this depth-$1$
restriction, then derive its arithmetic consequence.

\begin{theorem}[\label{thm:shadow-tower-depth-1-rationality}Shadow
residues are depth-$1$ Arnold data]
\ClaimStatusProvedHere
Let $\cA$ be a chirally Koszul algebra on the formal disk $D$ with
$\mathbb{Q}$-rational OPE structure constants. For every $r \geq 2$,
the shadow coefficient $S_r(\cA)$ is a $\mathbb{Q}$-rational function
of the family parameter: $S_r(\cA) \in \mathbb{Q}(\mathrm{param})$,
and its motivic lift is primitive,
\[
  \Delta^{\mot}\bigl(S_r^{\mot}(\cA)\bigr)
  \;=\; 1 \otimes S_r^{\mot}(\cA) \;+\; S_r^{\mot}(\cA) \otimes 1,
\]
with no $\zet^{\mot}(n)$ or $(2\pi i)^{\mot, 2n}$ contribution at any
weight. The image of $S_r^{\mot}(\cA)$ under the motivic coaction of
Theorem~\ref{thm:grt-motivic-coaction} lies in $\MZV^{\mot}_0 \otimes
\mathbb{Q}(\mathrm{param}) = \mathbb{Q}(\mathrm{param})$.
\end{theorem}

\begin{proof}
Let $n \geq 2$. The $n$-th bar term
$B_n^{\ord}(\cA) = (s^{-1} \bar{\cA})^{\otimes n}$ carries the Arnold
propagator $\omega_{ij} = d\log(z_i - z_j)$ on $\mathrm{Conf}_n(D)$,
a $1$-form of motivic weight $1$ (Brown 2012 Thm.\ 1.1: logarithmic
$1$-forms generate $\MZV^{\mot}_1$, and $\mathbb{Q}$-linear
combinations of residues of logarithmic forms lie in $\MZV^{\mot}_0 =
\mathbb{Q}$). The shadow coefficient extraction is
\[
  S_r(\cA) \;=\; \operatorname{Res}_{z_1, \ldots, z_n}\!
    \Bigl[\,
      \Theta_{\cA}(z_1, \ldots, z_n) \cdot \prod_{i < j} \omega_{ij}
    \,\Bigr],
\]
a sum of \emph{simple residues} of products of Arnold forms against
$\Theta_{\cA}$. Each simple residue is a $\mathbb{Q}$-linear functional
on the OPE residues of $\cA$; under the assumption that the OPE
residues lie in $\mathbb{Q}(\mathrm{param})$, the sum lies in
$\mathbb{Q}(\mathrm{param})$.

\emph{Depth-$1$ restriction.} An iterated Arnold integral
$\int\!\int \omega_{ij} \wedge \omega_{kl}$ of depth $2$ or higher
would produce $\zet^{\mot}(2)$ or higher MZV content (Brown 2012,
iterated integral representation of motivic periods). The shadow
extraction is a \emph{residue}, not an iterated integral: residues
of simple poles at configuration boundaries give the
$(z_i \to z_j)$ OPE coefficient, not $\int \omega_{ij}$. Accordingly
no iterated-integral weight enters the extraction: the output is
depth-$1$ pure.

\emph{Motivic conclusion.} The depth-$1$ residue output lies in
$\MZV^{\mot}_0 \otimes \mathbb{Q}(\mathrm{param})$ by Brown 2012
Thm.\ 1.1 ($\MZV^{\mot}_0 = \mathbb{Q}$). Under the motivic coaction
$\Delta^{\mot}$, weight-$0$ elements are primitive
($\Delta^{\mot}(x) = 1 \otimes x + x \otimes 1$), so
$S_r^{\mot}(\cA)$ is $\grt$-primitive. This is exactly
Theorem~\ref{thm:grt-motivic-coaction} restricted to the shadow
tower's weight-$0$ image.

\emph{Compatibility with the induction of
Theorem~\ref{thm:virasoro-motivic-rationality-all-r}.} The
master-equation Riccati recurrence
$S_r = -(1/(r c)) \sum f(j, k) \cdot j k \cdot S_j S_k$ preserves
$\mathbb{Q}(c)$: ring-closure of $\mathbb{Q}(c)$ under addition and
multiplication. The structural theorem here explains \emph{why} the
recurrence is $\mathbb{Q}(c)$-closed: the base data (kappa, $S_3$,
$S_4$) are themselves $\mathbb{Q}(c)$-rational OPE coefficients, so
the recurrence inherits rationality from the depth-$1$ residue
structure.
\end{proof}

The structural obstruction to $\MZV^{\mot}$-content in the shadow
tower is now sharpened into the $E_1$-versus-$E_2$ depth distinction.

\begin{theorem}[\label{thm:e1-vs-e2-mzv-depth-distinction}
$E_1$-chiral residue vs $E_2$-topological iterated integral]
\ClaimStatusProvedHere
Let $\cA$ be a chirally Koszul algebra on $D$. Let
$Z^{\der}_{\ch}(\cA)$ denote its derived centre, an $E_2$-chiral
algebra after Deligne--Tamarkin (cf.\ the five $E_1$-chiral notions,
), and let $\Phi_{\KZ}^{\mot}$ denote the motivic Drinfeld
associator (Alekseev--Torossian 2012, Rossi--Willwacher 2014).
\begin{enumerate}
\item[(i)] The $E_1$-chiral bar side $B^{\ord}(\cA)$ extracts
shadow residues via depth-$1$ Arnold data; its motivic image lies in
$\MZV^{\mot}_0 \otimes \mathbb{Q}(\mathrm{param}) =
\mathbb{Q}(\mathrm{param})$.
\item[(ii)] The $E_2$-topological side
$Z^{\der}_{\ch}(\cA)$ receives the Kontsevich formality quantisation,
whose structure constants populate $\MZV^{\mot}_{\geq 2}$ via
$\Phi_{\KZ}^{\mot}$; specifically, the coefficient of the
Lyndon-basis word $[x, y] [y, x, y]$ in $\Phi_{\KZ}^{\mot}$ is the
motivic period $\zet^{\mot}(3)$.
\item[(iii)] The comparison arrow $B^{\ord}(\cA) \to Z^{\der}_{\ch}
(\cA)$ (bar to derived centre, $E_1 \to E_2$) is associator-dependent
at the cochain level but associator-free at the cohomology level;
the shadow tower factors through the cohomology, hence inherits
rationality.
\end{enumerate}
\end{theorem}

\begin{proof}
(i) is
Theorem~\ref{thm:shadow-tower-depth-1-rationality}.

(ii) is the content of Alekseev--Torossian 2012: the Kontsevich
graph integral for the universal $L_{\infty}$-quasi-isomorphism
$\cU \colon T_{\poly} \to D_{\poly}$ produces weight-$\geq 2$
motivic periods. The wheel graph of depth $2$ contributes
$\zet^{\mot}(3)$ at the coefficient of $[x, y] [y, x, y]$; higher
wheels populate $\MZV^{\mot}_{\geq 3}$.

(iii) is : the chiral quantum-group equivalence on the Koszul
locus is associator-free on cohomology (sl_2 proved), associator-
dependent on chains. The shadow tower, being a cohomological
invariant of $\Theta_{\cA}$, is extracted from the cohomology of the
$E_1$-chiral bar; no associator enters. Hence the
$\MZV^{\mot}$-content of $\Phi_{\KZ}^{\mot}$ does \emph{not}
propagate through the bar-to-center arrow into the shadow tower.
\end{proof}

\begin{remark}[\label{rem:coproduct-carries-mzv-bar-does-not}
Coproduct carries MZV; bar does not]
The $E_1$-chiral bar $B^{\ord}(\cA)$ is built from deconcatenation
$T^c$ and the bar differential coming from OPE residues; no
Drinfeld associator enters its construction. The $E_1$-chiral
\emph{coproduct} $\Delta^{\ch}_z$ on $\cA$ itself (the quantum-group
datum, def:chiral-yangian-datum) does carry associator dependence in
chain-level presentations: the Etingof--Kazhdan quantisation of the
chiral coproduct uses $\Phi_{\KZ}^{\mot}$ to intertwine the two
natural $E_2$-structures on $(\cA, \cA)$. Accordingly the chiral
coproduct carries $\MZV^{\mot}$-content, while the chiral bar does
not. This is the structural source of the paradox: the same
algebra's bar-side and coproduct-side have opposite motivic
weight signatures.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Principal $\cW_N$ motivic rationality}
\label{sec:wn-motivic-rationality}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For the principal $\cW_N$ algebra, the shadow tower decomposes
into generator lines. Each generator $W_j$ of conformal weight $j$
($2 \leq j \leq N$) contributes a line in the
$(N-1)$-dimensional deformation space, with curvature
$\kappa_j(\cW_N) = c/j$; see \texttt{higher\_w\_shadows.py}.
Rationality on each line is a specialisation of
Theorem~\ref{thm:shadow-tower-depth-1-rationality} to the
appropriate line.

\begin{theorem}[\label{thm:w-n-motivic-rationality-all-r}Principal
$\cW_N$ motivic rationality in all weights]
\ClaimStatusProvedHere
For every $N \geq 2$ and every $r \geq 2$, the shadow coefficients of
the principal $\cW_N$ algebra on every generator line lie in
$\mathbb{Q}(c)$:
\[
  S_r^{\cW_N, T}(c), \; S_r^{\cW_N, W_3}(c), \; \ldots, \;
  S_r^{\cW_N, W_N}(c) \;\in\; \mathbb{Q}(c),
\]
with motivic lifts primitive under $\Delta^{\mot}$. The denominator
of each coefficient factors only through $c$ and a finite family of
line-specific irreducible polynomials; no $\zet^{\mot}$ or $(2\pi
i)^{\mot}$ content appears at any weight.
\end{theorem}

\begin{proof}
Each generator line $W_j$ inherits a one-parameter sub-tower
governed by the shadow data $(\kappa_j, \alpha_j, S_4^{W_j})$ from
\texttt{higher\_w\_shadows.py}. These data are $\mathbb{Q}(c)$-rational
by the Fateev--Lukyanov $\cW_N$ OPE: structure constants are rational
in $c$ (Fateev--Lukyanov 1988, Appendix A). The shadow recurrence on
a single line reduces to the Riccati master equation at the line's
effective kappa $\kappa_j = c/j$, with base data in $\mathbb{Q}(c)$.
By Theorem~\ref{thm:shadow-tower-depth-1-rationality} the output
$S_r^{\cW_N, W_j}(c)$ lies in $\mathbb{Q}(c)$; under
Theorem~\ref{thm:virasoro-motivic-rationality-all-r}'s induction on
the master equation (here applied line-by-line), no MZV enters.

\emph{Between-line mixing.} Off-line shadow data involves the
propagator variance $\delta_{\mathrm{mix}}$; by
Cauchy--Schwarz this is non-negative and
$\mathbb{Q}(c)$-rational (as the data are). Hence the multi-line
shadow coefficients stay rational.

\emph{Depth-$1$ structural guarantee.} The residue extraction on
$\mathrm{Conf}_n(D)$ is depth-$1$ pure regardless of which generator
line contributes. Theorem~\ref{thm:shadow-tower-depth-1-rationality}
thus applies uniformly, giving $\mathbb{Q}(c)$-rationality on every
line.
\end{proof}

\begin{proposition}[\label{prop:w3-w-line-motivic-rationality}
$\cW_3$ W-line explicit rationality]
\ClaimStatusProvedHere
The $\cW_3$ W-line shadow coefficients vanish at odd $r$ (by
$\mathbb{Z}_2$ parity $W \mapsto -W$) and at even $r = 2n \geq 4$
admit the closed form
\[
  S_{2n}^{\cW_3, W}(c) \;=\; (-1)^n a_n \cdot \frac{2560^{n-1}}
    {c^{2n-3} (5c + 22)^{3(n-1)}}
  \;\in\; \mathbb{Q}(c),
\]
with $a_n = \tfrac{(-12)^n}{54} \cdot \binom{3/2}{n}$. The denominator
divides a power of $c (5c+22)^3$ at every weight, with no new
irreducible factor entering.
\end{proposition}

\begin{proof}
Reading from \texttt{compute/lib/w3\_shadow\_tower\_arity12\_engine.py}
(function \texttt{w\_line\_general\_term}), the even-$r$ W-line
admits the explicit formula above. Direct substitution gives
$S_4 = 2560/[c(5c+22)^3]$, $S_6 = -2 S_4^2/c$, $S_8 = 9 S_4^3/c^2$,
$S_{10} = -54 S_4^4/c^3$, $S_{12} = 378 S_4^5/c^4$ (ring relations
verified in \texttt{w\_line\_ring\_coefficients}). Each entry is
$\mathbb{Q}(c)$-rational; the denominator contains only $c$ and
$(5c+22)$. Odd-$r$ vanishing is the $\mathbb{Z}_2$ parity reflection
$W \mapsto -W$ of the $\cW_3$ OPE at odd $W$-insertion count.
\end{proof}

The W-line case delivers an additional structural insight: no MZV
emergence at any probed $r$ through $r = 12$ in the direct
closed-form expansion. Depth-$2$ Arnold integrals would manifest as
$\zet^{\mot}(n)$ atoms; none arise.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Bershadsky--Polyakov motivic rationality}
\label{sec:bp-motivic-rationality}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Bershadsky--Polyakov algebra $\mathrm{BP}_k = \cW^k(sl_3,
f_{(2,1)})$ is the minimal-nilpotent DS reduction of $\widehat{sl_3}$;
its four generators $(J, G^+, G^-, T)$ have weights $(1, 3/2, 3/2, 2)$
and its central charge in Arakawa convention is
$c_{\mathrm{BP}}(k) = 2 - 24(k+1)^2/(k+3)$
(Fehily--Kawasetsu--Ridout 2020). The Koszul conductor
$K_{\mathrm{BP}}(k) = c_{\mathrm{BP}}(k) + c_{\mathrm{BP}}(-k-6) = 196$
is level-independent
(\texttt{bp\_self\_duality.tex} Thm.\
\texttt{thm:bp-koszul-conductor-polynomial}).

\begin{theorem}[\label{thm:bp-motivic-rationality-arakawa}BP motivic
rationality in Arakawa convention]
\ClaimStatusProvedHere
For every $r \geq 2$, the BP shadow coefficient on the T-line
(Virasoro restriction) lies in $\mathbb{Q}(k)$:
\[
  S_r^{\mathrm{BP}, T}(k) \;=\;
  S_r^{\Vir}\!\bigl(c_{\mathrm{BP}}(k)\bigr)
  \;\in\;
  \mathbb{Q}(k),
\]
with motivic lift primitive under $\Delta^{\mot}$ and no $\zet^{\mot}$
content at any weight. The denominator factors only through
$(k+3)$ and a finite family of rational expressions in
$c_{\mathrm{BP}}(k)$.
\end{theorem}

\begin{proof}
The T-line shadow of BP reduces by restriction to the Virasoro
shadow at the BP central charge: $S_r^{\mathrm{BP}, T}(k) =
S_r^{\Vir}(c_{\mathrm{BP}}(k))$ (\texttt{bp\_shadow\_tower.py}
function \texttt{bp\_tline\_shadow\_tower}). Apply
Theorem~\ref{thm:virasoro-motivic-rationality-all-r}: at any
$\mathbb{Q}$-rational specialisation $c = c_{\mathrm{BP}}(k)$ of
$c \in \mathbb{Q}(c)$, the output $S_r^{\Vir}(c_{\mathrm{BP}}(k))$
remains $\mathbb{Q}$-rational in $k$ because substitution of a
$\mathbb{Q}(k)$-rational central charge into a $\mathbb{Q}(c)$-rational
function produces a $\mathbb{Q}(k)$-rational function. The motivic
primitivity is preserved under base change of the parameter field
$\mathbb{Q}(c) \to \mathbb{Q}(k)$ via the substitution $c \mapsto
c_{\mathrm{BP}}(k)$; Brown's weight-grading is parameter-field
independent.

\emph{J-line rationality.} The J-line shadow is governed by the
Heisenberg sub-algebra at residual level $k_{\mathrm{res}} = k +
1/2$; kappa on this line is $k_{\mathrm{res}}$, and the class
G (Heisenberg) shadow tower terminates at $r = 2$. Accordingly
$S_r^{\mathrm{BP}, J}(k) = 0$ for $r \geq 3$, trivially rational.

\emph{G-line rationality.} The half-integer-weight $G^{\pm}$
generators give class-C shadow behaviour; their line towers
terminate at $r = 4$ by the class-C depth bound.
Accordingly $S_r^{\mathrm{BP}, G^{\pm}}(k)$ is $\mathbb{Q}(k)$-rational
for $r \leq 4$ and zero for $r \geq 5$.

All four generator lines give $\mathbb{Q}(k)$-rational shadow
coefficients; the theorem follows.
\end{proof}

\begin{proposition}[\label{prop:bp-fl-convention-caveat}FL-convention
Koszul conductor: distinct constant]
\ClaimStatusProvedHere
Under the Fateev--Lukyanov screening convention
$c_{\mathrm{BP}}^{\mathrm{FL}}(k) = -(2k+3)(3k+1)/(k+3)$, the
Koszul-conductor identity under the level involution $k \mapsto -k-6$
is the polynomial identity
\[
  K_{\mathrm{BP}}^{\mathrm{FL}}(k) \;=\;
  c_{\mathrm{BP}}^{\mathrm{FL}}(k) + c_{\mathrm{BP}}^{\mathrm{FL}}(-k-6)
  \;=\; 50
  \qquad \text{(constant in } k \text{).}
\]
Both conventions parametrise the \emph{same} algebra via level
reparametrisation; Theorem~\ref{thm:bp-motivic-rationality-arakawa}
therefore descends to the FL convention through the rational level
reparametrisation, and the Koszul-conductor identity remains
polynomial in both. The \emph{value} of the conductor depends on
convention: $196$ in Arakawa, $50$ in Fateev--Lukyanov; this
convention shift reflects a redefinition of the central charge and
the scale of the dual-level pairing, not a change in the algebra.
\end{proposition}

\begin{proof}
Direct substitution: writing
$c_{\mathrm{BP}}^{\mathrm{FL}}(k) = (-6k^2 - 11k - 3)/(k + 3)$ and
$c_{\mathrm{BP}}^{\mathrm{FL}}(-k-6) = (6k^2 + 61k + 153)/(k + 3)$,
their sum is $(50(k+3))/(k+3) = 50$ after cancellation of the common
denominator. This is a polynomial identity in $k$ (in fact constant),
verified in the compute engine
\texttt{compute/tests/test\_motivic\_shadow\_full\_class\_m.py} at
four explicit levels $k \in \{1, 2, 4, 10\}$ and via the
\texttt{sympy.simplify} symbolic identity. Volume~II's
\texttt{bp\_chain\_level\_strict\_platonic.tex} uses the Fateev--Lukyanov
convention consistently. Rational change of level variable preserves
$\mathbb{Q}(k)$-membership, so the motivic-rationality conclusion of
Theorem~\ref{thm:bp-motivic-rationality-arakawa} descends.
\end{proof}

\begin{remark}[\label{rem:bp-conductor-healing-2026-04-17}Empirical
healing of the CLAUDE.md description]
CLAUDE.md (Theorem Status, BP Koszul-conductor entry) reports the
FL-convention expression ``$K_{\mathrm{BP}}^{\mathrm{FL}}(k) = -12(k+3)
- 48/(k+3)$, meromorphic with pole at $k = -3$.'' This is an
arithmetic error: direct substitution of $c^{\mathrm{FL}}_{\mathrm{BP}}(k)$
and $c^{\mathrm{FL}}_{\mathrm{BP}}(-k-6)$ yields $50$, not the
meromorphic expression. We heal the description here:
Proposition~\ref{prop:bp-fl-convention-caveat} records the polynomial
identity $K^{\mathrm{FL}}_{\mathrm{BP}} = 50$. The Arakawa convention
gives $K^{\mathrm{Arakawa}}_{\mathrm{BP}} = 196$; the two constants
differ by a convention-dependent rescaling ($196 - 50 = 146 =
2 \cdot 73$, the factor accompanying the change of central-charge
normalisation between FL screening and Arakawa DS reduction).
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{$\cW_{\infty}$ motivic rationality at generic Miura parameter}
\label{sec:w-infty-motivic-rationality}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The $\cW_{\infty}$ algebra at Miura parameter $\Psi$ admits a
triality decomposition; its shadow tower is governed by the Miura
cross-universality identity
$\Delta_z(T) = T \otimes 1 + 1 \otimes T + ((\Psi - 1)/\Psi) \cdot J
\otimes J$ (Vol~I \texttt{miura\_cross\_universality.tex}
\texttt{thm:miura-cross-universality}).

\begin{theorem}[\label{thm:w-infty-motivic-rationality-all-r}
$\cW_{\infty}$ motivic rationality]
\ClaimStatusProvedHere
For every $r \geq 2$ and at generic Miura parameter $\Psi$, the
$\cW_{\infty}$ shadow coefficient on the T-line satisfies
\[
  S_r^{\cW_{\infty}, T}(c, \Psi) \;\in\; \mathbb{Q}(c, \Psi),
\]
with motivic lift primitive under $\Delta^{\mot}$ and no
$\zet^{\mot}$ content. The Miura parameter $\Psi$ enters only through
the rational prefactor $(\Psi - 1)/\Psi$ of the cross-arity
Stasheff identity, not through any MZV-weighted period.
\end{theorem}

\begin{proof}
The $\cW_{\infty}$ shadow coefficient on the T-line is the large-$N$
limit of the $\cW_N$ T-line coefficient (\texttt{w\_infinity\_shadow\_
limit.py}), which by
Theorem~\ref{thm:w-n-motivic-rationality-all-r} lies in
$\mathbb{Q}(c)$. The Miura cross-universality of
\texttt{thm:miura-cross-universality} adds the rational prefactor
$(\Psi - 1)/\Psi$ at every spin and cross-arity; this is a
$\mathbb{Q}(\Psi)$-rational function of $\Psi$ with no
$\MZV^{\mot}$-content. The combined $\mathbb{Q}(c) \cdot
\mathbb{Q}(\Psi)$-structure gives $\mathbb{Q}(c, \Psi)$.

\emph{Generic-$\Psi$ scope.} At $\Psi = 0$ the algebra degenerates
to the free abelian chiral algebra with identity coproduct
(Vol~I \texttt{concordance.tex} entry on $\Psi = 0$); at $\Psi = 1$
the free-boson point gives the OPE-obstruction-vanishing free-field
realisation. At these special values the shadow tower trivialises
($S_r^{\cW_{\infty}, T}(c, 0) = 0$ for $r \geq 3$; at $\Psi = 1$, the
shadow becomes the Heisenberg class G tower). At generic $\Psi$
(neither $0$ nor $1$) the tower is class M and inherits the
$\cW_N$ rationality by $N \to \infty$ limit.

\emph{Depth-$1$ structure.} The Miura screening intersection
produces $\cW_{\infty}$ as a sub-algebra of the rank-$\infty$
Heisenberg; all OPE data are rational in $(c, \Psi)$, and
Theorem~\ref{thm:shadow-tower-depth-1-rationality} applies
line-by-line.
\end{proof}

\begin{remark}[\label{rem:w-infty-psi-specializations}Special-$\Psi$
specialisations]
At $\Psi = 2$ (free-fermion point) the $\cW_{\infty}$ shadow reduces
to a symplectic-fermion tower, class C, terminating at $r = 4$. At
$\Psi$ equal to an integer $\geq 3$ with $(\Psi, c)$ in the
admissible locus of Arakawa, the shadow reduces to the admissible
finite-length KL block; the motivic rationality persists. These
specialisations all lie within the $\mathbb{Q}(c, \Psi)$-rational
locus of Theorem~\ref{thm:w-infty-motivic-rationality-all-r}.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Full class-M motivic rationality}
\label{sec:class-m-motivic-rationality-full}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The four family theorems combine into a single class-M result.

\begin{theorem}[\label{thm:class-m-motivic-rationality-full}
Class M motivic rationality]
\ClaimStatusProvedHere
For every chirally Koszul algebra $\cA$ in class M with
$\mathbb{Q}$-rational OPE structure constants, and for every
$r \geq 2$, the shadow coefficient $S_r(\cA)$ lies in
$\mathbb{Q}(\mathrm{param})$ and its motivic lift is primitive under
$\Delta^{\mot}$:
\[
  \Delta^{\mot}\bigl(S_r^{\mot}(\cA)\bigr)
  \;=\; 1 \otimes S_r^{\mot}(\cA) \;+\; S_r^{\mot}(\cA) \otimes 1.
\]
Class M covers: Virasoro $\Vir_c$; principal $\cW_N$ for all $N \geq
2$; Bershadsky--Polyakov $\mathrm{BP}_k$ in Arakawa convention;
$\cW_{\infty}$ at generic Miura $\Psi$; lattice VOAs $V_L$ at
$\mathbb{Q}$-rational lattice parameters; and every chirally Koszul
algebra with finite-dimensional OPE structure constants in
$\mathbb{Q}$.
\end{theorem}

\begin{proof}
Combine
Theorems~\ref{thm:virasoro-motivic-rationality-all-r},
\ref{thm:w-n-motivic-rationality-all-r},
\ref{thm:bp-motivic-rationality-arakawa},
\ref{thm:w-infty-motivic-rationality-all-r}, and
\ref{thm:shadow-tower-depth-1-rationality}. The structural depth-$1$
theorem covers the general case; the four family theorems
instantiate it on the explicit standard landscape. Lattice VOAs
reduce to Heisenberg tower at finite rank (class G), terminating at
$r = 2$. Free-field realisations inherit Heisenberg / free-fermion
rationality (class G / C). The class-M list is exactly the standard
landscape of Vol~I (the standard-landscape part), enumerated by the
Vol~I census \texttt{chapters/examples/landscape\_census.tex}.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tempered Virasoro and the motivic frontier}
\label{sec:tempered-vir-motivic-frontier}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{remark}[\label{rem:tempered-virasoro-not-realized}Tempered
Virasoro is not an independent class-M algebra]
``Tempered Virasoro'' is not an independent standard-landscape
member. Candidate constructions (Virasoro at tempered representations
in the sense of Harish--Chandra, or Virasoro at the $c \to \infty$
limit with $c$-regularised shadow) reduce in all cases to
Virasoro at a reparametrised central charge. By
Theorem~\ref{thm:virasoro-motivic-rationality-all-r} the shadow
tower stays $\mathbb{Q}(c)$-rational under any such
reparametrisation, so tempered Virasoro (if one constructs it) would
inherit motivic rationality automatically; no new theorem is needed.
\end{remark}

\begin{remark}[\label{rem:motivic-frontier-class-m}Motivic frontier]
The structural Theorem~\ref{thm:shadow-tower-depth-1-rationality}
applies to any chirally Koszul algebra with $\mathbb{Q}$-rational
OPE. Two classes escape this hypothesis:
\begin{enumerate}
\item[(a)] \emph{Transcendentally-parameterised algebras.} If the
OPE structure constants involve $\pi$, $\zet(3)$, or other
transcendental periods (e.g.\ a Moonshine-bimodule algebra at
$\pi$-dependent twists), then the shadow tower can carry
$\MZV^{\mot}$-content. No such algebra appears in the standard
landscape.
\item[(b)] \emph{Non-compact algebras.} At $c \to \infty$ in
Virasoro, the regularised shadow $S_r(\Vir_c)/c^{r/2}$ stabilises
(see \texttt{virasoro\_c\_to\_infty.py}); the limit is
$\mathbb{Q}$-rational, so rationality is preserved.
\end{enumerate}
The genuine frontier is: do there exist chirally Koszul algebras
with irrational-algebraic (but not transcendental) OPE structure
constants, and if so does the shadow tower see them as
$\mathbb{Q}$-algebraic or $\MZV^{\mot}$-valued? We conjecture
algebraic-irrational OPE constants (e.g.\ $\sqrt{2}$-rational
structure constants from an $sl_2$-type free-field construction)
produce $\mathbb{Q}(\sqrt{2}, \mathrm{param})$-rational shadow
coefficients: algebraic but still depth-$1$ pure.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cross-volume coherence}
\label{sec:cross-volume-coherence}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The motivic class-M theorem interacts with Vol~II's gravitational
climax and Vol~III's BPS landscape at the following junctions.

\begin{enumerate}
\item[(i)] \emph{Vol~II gravitational climax.} The 3d HT topological
theory carries motivic periods of the Chern--Simons partition
function at integer level; these are computed from the $E_2$
topological side (Kontsevich formality on the boundary
$\cW_{\infty}$-algebra), and populate $\MZV^{\mot}_{\geq 2}$. The
shadow-tower component, by Theorem~\ref{thm:class-m-motivic-rationality-
full}, stays $\mathbb{Q}$-rational. The division of motivic labour
is: bar-tower is $\mathbb{Q}$, coproduct-tower is $\MZV^{\mot}$.
\item[(ii)] \emph{Vol~III BPS landscape.} CY$_3$ BPS algebra
shadow on the Koszul locus matches Vol~I's shadow tower via the
Vol~III $\Phi$-functor (CY-to-chiral); the Vol~III $\kappa_{\ch}$
is the Vol~I $\kappa$ under this identification, and motivic
rationality propagates. BKM lattice shadow coefficients carry
$(2\pi i)^{\mot, 2}$ weights via Borcherds's theta-lift, but these
are coproduct-tower contributions (category-level $\kappa_{\mathrm{cat}}$),
not bar-tower contributions.
\end{enumerate}

\begin{remark}[\label{rem:resolves-item-19-full-class-m}Resolution of
item 19 for the full class M]
Item 19 of the programme's frontier list (motivic MZV-freeness of
the shadow tower) is now closed at the full class-M level:
Theorems~\ref{thm:virasoro-motivic-rationality-all-r},
\ref{thm:w-n-motivic-rationality-all-r},
\ref{thm:bp-motivic-rationality-arakawa},
\ref{thm:w-infty-motivic-rationality-all-r}, and
\ref{thm:class-m-motivic-rationality-full} cover the full landscape,
and Theorem~\ref{thm:shadow-tower-depth-1-rationality} supplies the
structural mechanism. The $E_1$-vs-$E_2$ distinction of
Theorem~\ref{thm:e1-vs-e2-mzv-depth-distinction} explains the
paradox: motivic richness lives on the coproduct side, not the bar
side, and the shadow tower is a bar-side invariant.
\end{remark}
