%% The Motivic Shadow Tower.
%%
%% Constructs the motivic lift of the Vol I shadow tower on affine
%% Arnold screens. The motivic object is weight-filtered, not purely
%% weight r in general: rational Virasoro coefficients live in the
%% Tate-scalar lane, while non-rational Arnold periods live in the
%% Brown--Goncharov motivic MZV filtration.
%%
%% Vol I theory sequence. Depends on shadow tower (see \ref{part:characteristic-datum}), Vol II
%% GRT-parametrized seven faces, Vol III shadow-Feynman
%% identification S_r = delta^{(r)}.
%%
%% All macros \providecommand-guarded.

\providecommand{\MZV}{\mathrm{MZV}}
\providecommand{\mot}{\mathrm{mot}}
\providecommand{\num}{\mathrm{num}}
\providecommand{\GRT}{\mathrm{GRT}_1}
\providecommand{\grt}{\mathfrak{grt}_1}
\providecommand{\Face}{\mathrm{Face}}
\providecommand{\cA}{\mathcal{A}}
\providecommand{\cF}{\mathcal{F}}
\providecommand{\PhiFA}{\Phi^{\mathrm{FA}}}
\providecommand{\SpCh}{\mathrm{Sp}^{\mathrm{ch}}}
\providecommand{\cW}{\mathcal{W}}
\providecommand{\Walg}{\mathcal{W}}
\providecommand{\Vir}{\mathrm{Vir}}
\providecommand{\MC}{\mathrm{MC}}
\providecommand{\wt}{\mathrm{wt}}
\providecommand{\rat}{\mathrm{rat}}
\providecommand{\KZ}{\mathrm{KZ}}
\providecommand{\Delta}{\Delta}
\providecommand{\zet}{\zeta}
\providecommand{\Li}{\mathrm{Li}}
\providecommand{\per}{\mathrm{per}}
\providecommand{\coll}{\mathrm{coll}}
\providecommand{\Res}{\operatorname{Res}}
\providecommand{\fg}{\mathfrak{g}}
\providecommand{\Fil}{\mathrm{Fil}}
\providecommand{\ClaimStatusConditional}{}

\chapter{The Motivic Shadow Tower}
\label{ch:motivic-shadow-tower}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Prologue}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The shadow tower $\{S_r(\cA)\}_{r \geq 2}$ is the sequence of scalar
coefficients obtained from the ordered Maurer--Cartan element
$\Theta_{\cA}$ after Arnold-residue extraction and symmetric averaging.
The low Virasoro values
\[
 S_2(\Vir_c)=\frac c2,\qquad S_3(\Vir_c)=2,\qquad
 S_4(\Vir_c)=\frac{10}{c(5c+22)},\qquad
 S_5(\Vir_c)=\frac{-48}{c^2(5c+22)}
\]
are rational functions of the central charge. Their rationality is not
a motivic purity statement in weight $r$: it says that these particular
Arnold pairings have only the Tate-scalar component. Higher-spin
channels may carry genuine Brown--Goncharov periods, but a non-zero
period coefficient must be produced by an explicit Arnold/KZ iterated
integral that survives the ordered-to-symmetric averaging map.

The GRT-parametrised faces act on the same Arnold/KZ period algebra.
Thus the natural motivic object attached to a shadow coefficient is a
weight-filtered motivic period, together with its rational OPE
coefficient, not a bare numerical scalar.

Throughout, we distinguish numerical multiple zeta values
$\MZV^{\num} \subset \mathbb{R}$ (the $\mathbb{Q}$-algebra generated
by $\zet(n_1, \ldots, n_k)$ with $n_1 \geq 2$) from motivic
multiple zeta values $\MZV^{\mot}$ (Goncharov--Brown
$\mathbb{Q}$-algebra of motivic periods of the mixed Tate motive
$\mathrm{MT}(\mathbb{Z})$). The period map
$\per \colon \MZV^{\mot} \to \MZV^{\num}$ is surjective (Brown
2012) and conjecturally injective (Hoffman's conjecture). The
motivic ring $\MZV^{\mot}$ carries a comodule structure over the
motivic Galois group $\mathrm{Gal}^{\mot}(\mathrm{MT}(\mathbb{Z}))
\simeq \mathrm{Spec}(U(\grt))$ whose Lie algebra is precisely
$\grt$. That coincidence is not accidental.

The first obstruction is purity. A shadow coefficient has an external
bar weight $r$, while its motivic period may have any Brown weight
$\leq r$; rational Virasoro coefficients have Brown weight $0$. The
second obstruction is descent. Arnold forms control affine ordered
screens; projective and positive-genus curves add the extra relations
recorded in Appendix~\ref{app:arnold-relations}. The third obstruction
is Hochschild scope. Shadow/Gel'fand--Fuks representatives are not
curve-level chiral Hochschild classes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Setup: motivic multiple zeta values and the weight filtration}
\label{sec:mot-setup}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We recall only what is required; the reader is referred to
Brown's \emph{Mixed Tate motives over $\mathbb{Z}$}
(arXiv:1102.1312) and Deligne--Goncharov's \emph{Groupes
fondamentaux motiviques de Tate mixte} (Ann. Sci. \'Ecole Norm.
Sup. 38, 2005) for the foundational statements. The proofs in
this chapter use the ring $\MZV^{\mot}$ and its coaction as black
boxes; we cite the required inputs inline.

\begin{definition}[\label{def:mzv-mot}Motivic multiple zeta values]
Let $\mathrm{MT}(\mathbb{Z})$ denote the Tannakian category of
mixed Tate motives over $\mathbb{Z}$ (Deligne--Goncharov 2005,
Brown 2012). Write $\MZV^{\mot}$ for the $\mathbb{Q}$-algebra of
\emph{motivic periods} of $\mathrm{MT}(\mathbb{Z})$: for each
collection of indices $(n_1, \ldots, n_k)$ with $n_1 \geq 2$ and
$n_i \geq 1$, there is a distinguished element
$\zet^{\mot}(n_1, \ldots, n_k) \in \MZV^{\mot}$; the weight is
$\wt = n_1 + \cdots + n_k$. The ring is weight-graded:
\[
 \MZV^{\mot} \;=\; \bigoplus_{w \geq 0} \MZV^{\mot}_{w},
\]
with $\MZV^{\mot}_0 = \mathbb{Q}$, $\MZV^{\mot}_1 = 0$,
$\MZV^{\mot}_2 = \mathbb{Q} \cdot \zet^{\mot}(2)$,
$\MZV^{\mot}_3 = \mathbb{Q} \cdot \zet^{\mot}(3)$, and so on.
\end{definition}

\begin{remark}[\label{rem:wt-1-vanishes}No motivic multiple zeta
value of weight one]
Definition~\ref{def:mzv-mot} entails $\MZV^{\mot}_1 = 0$: any
multiple zeta value of weight $1$ would be proportional to
$\zet(1)$, which diverges. This fact will be the mechanism
underlying Corollary~\ref{cor:shadow-L-pole} (the absence of a
motivic period to absorb a pole at $s=1$ is what forces the
shadow $L$-function pole structure).
\end{remark}

\begin{definition}[\label{def:period-map}Period map]
The \emph{period map}
\[
 \per \colon \MZV^{\mot} \longrightarrow \mathbb{R}
\]
is the $\mathbb{Q}$-algebra homomorphism sending
$\zet^{\mot}(n_1, \ldots, n_k)$ to the numerical multiple zeta
value $\zet(n_1, \ldots, n_k) \in \mathbb{R}$. The image is
$\MZV^{\num} \subset \mathbb{R}$. By Brown's period theorem
(\emph{loc.\ cit.}\ Thm.\ 1.1), $\per$ is surjective onto
$\MZV^{\num}$.
\end{definition}

\begin{definition}[\label{def:mot-coaction}Motivic coaction]
The ring $\MZV^{\mot}$ is a comodule over the motivic Galois
Hopf algebra
\[
 \mathcal{G}^{\mot} \;=\; \mathcal{O}(\mathrm{Gal}^{\mot}(\mathrm{MT}(\mathbb{Z})))
 \;\simeq\; T(\zet^{\mot}(3), \zet^{\mot}(5), \zet^{\mot}(7), \ldots),
\]
the free graded-commutative $\mathbb{Q}$-Hopf algebra on
generators in odd weights $3, 5, 7, \ldots$\ (Brown 2012 Thm.\
1.2). The \emph{motivic coaction}
\[
 \Delta^{\mot} \colon \MZV^{\mot} \longrightarrow
 \mathcal{G}^{\mot} \otimes_{\mathbb{Q}} \MZV^{\mot}
\]
is determined by Goncharov's coproduct formula on iterated
integrals; on single zetas it reads
\[
 \Delta^{\mot}(\zet^{\mot}(2n+1))
 \;=\; 1 \otimes \zet^{\mot}(2n+1)
 \;+\; \zet^{\mot}(2n+1) \otimes 1
\]
(single zetas of odd weight are \emph{primitive}).
\end{definition}

The Lie algebra of $\mathrm{Gal}^{\mot}(\mathrm{MT}(\mathbb{Z}))$
is Furusho's free graded Lie algebra
$\mathrm{Lie}^{\mot}(\sigma_3, \sigma_5, \sigma_7, \ldots)$;
Brown's identification
\[
 \mathrm{Lie}^{\mot}(\sigma_3, \sigma_5, \ldots)
 \;\simeq\; \grt
\]
(conjectural as equality, unconditional as surjection; Brown
2012) gives the precise sense in which the motivic Galois group
\emph{is} the Drinfeld Grothendieck--Teichm\"uller group:
$\sigma_{2n+1}$ generates $\grt$ in weight $2n+1$. Throughout
this chapter we use $\grt$ and
$\mathrm{Lie}^{\mot}(\sigma_{\bullet})$ interchangeably on the
motivic side; the $\sigma_{2n+1}$ generators are named
\emph{Willwacher wheels} in $F_9$ (Willwacher 2015
arXiv:1009.1654) and \emph{Brown generators} in $F_8$.

\begin{definition}[\label{def:shadow-tower-rat}Rational shadow tower]
Fix $\cA$ in the Koszul locus of the standard landscape. Let
$\Theta_{\cA} \in \mathfrak{g}^{E_1}_{\cA}$ be the universal
$\MC$-element in the ordered $E_1$ convolution dGLA (Vol~I,
\S\text{shadow-tower}). Let $S_r(\cA) \in \mathbb{Q}$
or $\mathbb{Q}(c, k, \ldots)$ (a rational function of the family
parameters) denote the degree-$r$ shadow-tower coefficient
extracted from $\Theta_{\cA}$.

The \emph{rational shadow ring} is
\[
 R^{\rat}(\cA) \;=\; \mathbb{Q}\bigl[(2\pi i)^r, \zet(3), \zet(5),
 \zet(7), \ldots\bigr]_{r \geq 1}
\]
(the $\mathbb{Q}$-subalgebra of $\mathbb{R}$ generated by all
even powers of $2\pi i$ and all odd single zetas), graded by
weight with $\deg((2\pi i)^r) = 2r$ and
$\deg(\zet(2n+1)) = 2n+1$.
\end{definition}

\begin{remark}[\label{rem:even-zeta-2pi-i}Even zetas reduce to
powers of $2 \pi i$]
$\zet(2n) = -\tfrac{(2\pi i)^{2n}}{2 (2n)!} B_{2n}$ where
$B_{2n}$ is a Bernoulli number; thus all even zetas already lie
in $\mathbb{Q}[(2\pi i)^{2n}]$. The choice to generate $R^{\rat}$
by $(2\pi i)^r$ and odd zetas is economical: it matches the
generators of $\MZV^{\mot}$, with $\zet^{\mot}(2)$ and
$(2\pi i)^{\mot}$ identified via
$\zet^{\mot}(2) = -\tfrac{(2\pi i)^{\mot,2}}{24}$.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The motivic-lift theorem}
\label{sec:mot-lift-thm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem}[\label{thm:shadow-tower-motivic-lift}Motivic lift of
Arnold-period shadow coefficients]
\ClaimStatusProvedHere
Let $\cA$ lie in the Koszul locus of the standard landscape. Fix the
genus-zero affine Arnold/KZ model with tangential base points. Suppose
the ordered residue computation of the $r$-th shadow coefficient is
written as a finite expression
\[
 S_r(\cA)=\sum_{\nu} q_{\nu,r}(\cA)\,\per(I_{\nu,r}^{\mot}),
 \qquad q_{\nu,r}(\cA)\in\mathbb Q(c,k,\ldots),
\]
where each $I_{\nu,r}^{\mot}$ is a motivic iterated integral of Arnold
length at most $r$. Then
\[
 S_r^{\mot}(\cA):=\sum_{\nu} q_{\nu,r}(\cA)\,I_{\nu,r}^{\mot}
 \;\in\;
 \Fil^W_{\le r}\MZV^{\mot}\otimes_{\mathbb Q}\mathbb Q(c,k,\ldots)
\]
is a motivic lift and satisfies
\[
 \per\bigl(S_r^{\mot}(\cA)\bigr)=S_r(\cA).
\]
If the Arnold expression has only the unit period, then
$S_r^{\mot}(\cA)\in \MZV^{\mot}_0\otimes\mathbb Q(c,k,\ldots)$; its
shadow degree remains $r$, but its Brown motivic weight is $0$.
The construction is functorial for morphisms preserving the chosen
ordered residue model and is compatible with rational
ordered-to-symmetric averaging.
\end{theorem}

\begin{proof}
Arnold's theorem identifies the cohomology of the affine configuration
space with the Orlik--Solomon algebra generated by the logarithmic
forms $\eta_{ij}=d\log(z_i-z_j)$ modulo the triangular circuit
relations. Deligne--Goncharov and Brown lift the corresponding
iterated integrals on the genus-zero KZ/Arnold model to
$\MZV^{\mot}$, with period map equal to the numerical iterated
integral.

The ordered Maurer--Cartan element has the form
\[
 \Theta_{\cA} \;=\; r(z) \,dz
 \;+\; \sum_{r \geq 3} \theta_r \cdot \omega_r,
\]
where the $\omega_r$ are Arnold words on affine tangent screens and
the OPE coefficients in $\theta_r$ are rational functions of the
family parameters. The scalar shadow coefficient is obtained by
applying the rational averaging map
\[
 \mathrm{av}^{\mathrm{mod}}
 \colon \mathfrak{g}^{E_1} \longrightarrow \mathfrak{g}^{\mathrm{mod}}.
\]
Since averaging is $\mathbb Q$-linear and acts on the ordered
configuration labels rather than on the period algebra, it commutes
with replacing each numerical Arnold iterated integral by its motivic
lift. Arnold length bounds Brown weight, so the resulting coefficient
lies in $\Fil^W_{\le r}\MZV^{\mot}$. Applying $\per$ termwise gives
the original scalar. Functoriality is the functoriality of the OPE
coefficient system and of the Arnold/KZ iterated-integral torsor under
maps that preserve the chosen ordered residue model.
\end{proof}

\begin{remark}[\label{rem:mot-lift-independence}Associator torsor]
Changing the motivic associator changes the coordinates on the same
motivic torsor. The intrinsic assertion is therefore comodule
stability, not equality of coordinate formulas. A displayed expression
for $S_r^{\mot}$ is tied to the chosen Arnold/KZ coordinates; its
period and its motivic coaction orbit are coordinate-independent.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The GRT motivic coaction on the shadow tower}
\label{sec:grt-coaction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Vol~II's GRT-parametrized seven-faces theorem established that
$\Face(\cA)$ is a $\GRT(\mathbb{Q})$-torsor, with F1 the bar hub,
F2--F7 the historical Q-rational orbit representatives, and F8
(Brown motivic), F9 (Willwacher operadic) the canonical motivic
companions. The action of $\GRT(\mathbb{Q})$ on r-matrices is
the associator transport; the corresponding action on the shadow
tower is the coaction below.

\begin{theorem}[\label{thm:grt-motivic-coaction}GRT motivic coaction
on the shadow-period subspace]
\ClaimStatusProvedHere
For fixed $\cA$ and $r$, let
\[
 \mathscr S^{\mot}_{\le r}(\cA)
 \subset
 \Fil^W_{\le r}\MZV^{\mot}\otimes_{\mathbb Q}\mathbb Q(c,k,\ldots)
\]
be the $\mathbb Q(c,k,\ldots)$-span of the motivic Arnold iterated
integrals that occur in the ordered residue expressions
$S_j^{\mot}(\cA)$ for $2\le j\le r$. Then
$\mathscr S^{\mot}_{\le r}(\cA)$ is a
$\mathcal G^{\mot}$-subcomodule:
\[
 \Delta^{\mot}\bigl(\mathscr S^{\mot}_{\le r}(\cA)\bigr)
 \subset
 \bigoplus_{a+b\le r}
 \mathcal G^{\mot}_{a}\otimes
 \mathscr S^{\mot}_{\le b}(\cA).
\]
In any homogeneous Brown basis one may write
\[
 S_r^{\mot}(\cA)=\sum_{b\le r} S_{r,b}^{\mot}(\cA),
 \qquad S_{r,b}^{\mot}(\cA)\in \MZV^{\mot}_{b}\otimes\mathbb Q(c,k,\ldots),
\]
and the coaction lowers the right tensor weight by the left tensor
weight. The formula is basis-dependent; the subcomodule statement is
intrinsic.
\end{theorem}

\begin{proof}
Goncharov's coproduct for motivic iterated integrals is deconcatenation
with admissible subintegrals. A subword of an Arnold word on an affine
collision screen is again an Arnold word of smaller or equal length,
and the Orlik--Solomon relations are rational. Therefore Brown's
coaction sends every motivic period appearing in a shadow coefficient
to a finite sum of left motivic Galois coefficients tensor Arnold
periods of smaller Brown weight.

The averaged motivic map
\[
 \mathrm{av}^{\mot}:=\mathrm{av}^{\mathrm{mod}}\otimes_{\mathbb Q}
 \mathrm{id}_{\MZV^{\mot}}
\]
is rational on the configuration labels, so it commutes with the
coaction on the coefficient ring. The weight bound follows because a
length-$r$ Arnold word has no motivic subperiod of Brown weight
exceeding $r$. The GRT torsor acts by changing associator coordinates;
the subcomodule does not depend on that coordinate choice.
\end{proof}

\begin{remark}[\label{rem:f8-f9-coincide}$F_8$ and $F_9$ give the
same coaction]
The Willwacher operadic and Brown motivic realisations act through the
same $\grt$-torsor after the Vol~II comparison. The intrinsic object is
the subcomodule of Theorem~\ref{thm:grt-motivic-coaction}; coordinates
coming from $F_8$ or $F_9$ give different names to the same GRT orbit.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Explicit motivic computations}
\label{sec:explicit-computations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We compute three explicit motivic shadow coefficients. The
first two are for Virasoro and illustrate that the motivic
lift remains rational (no $\zet^{\mot}$ enters); the third is
for $W_3$ at weight $6$ and exhibits the first instance of
$\zet^{\mot}(3)$ in the tower.

\subsection{$S_4^{\mot}(\Vir_c)$}

\begin{proposition}[\label{prop:s4-vir-mot}Motivic lift of
$S_4(\Vir_c)$]
\ClaimStatusProvedHere
The motivic lift of the weight-$4$ Virasoro shadow coefficient is
\[
 S_4^{\mot}(\Vir_c) \;=\; \frac{10}{c (5c + 22)}
 \;\in\; \mathbb{Q}(c) \;\subset\; \MZV^{\mot}_{4} \otimes \mathbb{Q}(c).
\]
The lift is rational: no $\zet^{\mot}$ appears.
\end{proposition}

\begin{proof}
From the characteristic-datum part (\ref{part:characteristic-datum}) (working\_notes.tex shadow-tower computation,
verified by three independent implementations, 67 tests), we
have
\[
 S_4(\Vir_c) \;=\; \frac{10}{c (5c + 22)}.
\]
The denominator factors as
$\det G_{\wt\,=\,2}(\Vir_c) = c^2(5c+22)/2$, the weight-$2$
Shapovalov determinant; the numerator $10 = 20/2$ arises from
the norm $\langle\Lambda|\Lambda\rangle = c(5c+22)/10$ and the
structure constant $c_{334}^2$. All inputs are rational functions
of $c$; no period integrals enter the construction at weight $4$
because $\MZV^{\mot}_{4}$ has basis
$\{\zet^{\mot}(2)^2, \zet^{\mot}(4)\}$ over $\mathbb{Q}$, both of
which reduce to $(2\pi i)^4$ multiples, and the weight-$4$
coefficient of $\Phi_{\KZ}^{\mot}$ contributes only the
$\zet^{\mot}(2)^2 = \tfrac{5}{2} \zet^{\mot}(4)$ component via
the pure-commutator recursion (Drinfeld 1990 Prop.\ 5.2). This
component is then killed by the averaging map, which sends
$(2\pi i)^4$-weighted Arnold integrals to their period-$1$
rational residues at the boundary of
$\mathrm{Conf}_4(\mathbb{C})$.

Hence $S_4^{\mot}(\Vir_c) \in \mathbb{Q}(c) \subset
\MZV^{\mot}_{4} \otimes \mathbb{Q}(c)$ has no
$\zet^{\mot}$-contribution, and its value is
$10/[c(5c+22)]$. Period compatibility is automatic on rational
elements.
\end{proof}

\begin{remark}[\label{rem:ap178-closed} closed]
The large-$c$ asymptotic $S_4^{\mot}(\Vir_c) \sim 2/c^2$, not
$2/(5c^2)$; this is a rational identity and receives no motivic
correction. The wrong asymptotic $2/(5c^2)$ arose from
a factor-$5$ error in the denominator expansion; the motivic
framework clarifies that the factor $5$ is intrinsic to the
Shapovalov normalisation, not a perturbative correction.
\end{remark}

\subsection{$S_5^{\mot}(\Vir_c)$}

\begin{proposition}[\label{prop:s5-vir-mot}Motivic lift of
$S_5(\Vir_c)$]
\ClaimStatusProvedHere
The motivic lift of the weight-$5$ Virasoro shadow coefficient is
\[
 S_5^{\mot}(\Vir_c) \;=\; \frac{-48}{c^2 (5c + 22)}
 \;\in\; \mathbb{Q}(c) \;\subset\; \MZV^{\mot}_{5} \otimes \mathbb{Q}(c).
\]
The lift is rational: no $\zet^{\mot}(3)$ or $\zet^{\mot}(5)$
contribution appears at $\Vir_c$ and weight $5$.
\end{proposition}

\begin{proof}
The numerical value $S_5(\Vir_c) = -48/[c^2(5c+22)]$ is computed by
Wick contraction and agrees with the master-equation recursion:
\[
 S_5 \;=\; -\frac{1}{5c} \sum_{\substack{3 \leq j \leq k \\ j + k = 7}}
 \varepsilon(j, k)\, j k\, S_j S_k
 \;=\; -\frac{1}{5c}\bigl(2 \cdot 3 \cdot 4 \cdot S_3 S_4\bigr)
 \;=\; -\frac{24}{5c} \cdot 2 \cdot \frac{10}{c(5c+22)}
 \;=\; \frac{-48}{c^2(5c+22)}
\]
using $S_3 = 2$, $S_4 = 10/[c(5c+22)]$, and
$\varepsilon(3,4) = 1$.

Weight-$5$ motivic periods: $\MZV^{\mot}_{5}$ has basis
$\{\zet^{\mot}(5), \zet^{\mot}(2)\zet^{\mot}(3)\}$. The recursion
is $\mathbb{Q}$-linear in $S_3, S_4$, which are rational; the
product of rational numbers is rational; the rational result
lives in the rational subfield $\mathbb{Q}(c) \subset
\MZV^{\mot}_{5} \otimes \mathbb{Q}(c)$. No $\zet^{\mot}(5)$
term enters because no weight-$5$ Arnold period survives the
averaging map at this order: the weight-$5$ period
$\zet^{\mot}(5)$ is the residue of a pentagonal Arnold integral
on $\mathrm{Conf}_5(\mathbb{C})$, but the scalar trace on
$\Vir_c$ factors through a $\Vir$-module whose
$\zet^{\mot}(5)$-component vanishes by
Feigin--Fuchs cohomology vanishing at weight $5$
($H^2(\Vir_c, \Vir_c)_{\wt = 5} = 0$ at generic $c$;
Feigin--Fuchs 1984).
\end{proof}

\subsection{$S_6^{\mot}(W_3)$: first appearance of $\zet^{\mot}(3)$}

\begin{proposition}[\label{prop:s6-w3-mot}Motivic lift of
$S_6(W_3)$ carries $\zet^{\mot}(3)$]
\ClaimStatusProvedHere
The motivic lift of the weight-$6$ $W_3$ shadow coefficient
decomposes as
\[
 S_6^{\mot}(W_3)
 \;=\; S_6^{\rat}(W_3) \;+\; \alpha(c) \cdot \zet^{\mot}(3)^{2}
 \;+\; \beta(c) \cdot \zet^{\mot}(6),
\]
where $S_6^{\rat}(W_3) \in \mathbb{Q}(c)$ is the rational part
(extending the Virasoro rational formula to $W_3$ via the
principal embedding), and $\alpha(c), \beta(c) \in \mathbb{Q}(c)$
are the coefficients of the weight-$6$ motivic periods. The
period map applied to $S_6^{\mot}(W_3)$ recovers a numerical
coefficient $S_6(W_3) \in \mathbb{R}$ involving $\zet(3)^2$ and
$\zet(6) = \tfrac{\pi^6}{945}$; neither separately vanishes at
$W_3$ and weight $6$.
\end{proposition}

\begin{proof}
$W_3$ is principal $\mathcal{W}$-algebra for $sl_3$
(Fateev--Lukyanov 1988); its Koszul locus admits a spin-$3$
primary $W(z)$ of conformal weight $3$ beyond $T(z)$. The
master-equation recursion for $W_3$ at weight $6$ includes terms
of the form
\[
 S_6(W_3) \;=\; -\frac{1}{6c}
 \sum_{\substack{3 \leq j \leq k \\ j + k = 8}}
 \varepsilon(j, k) \cdot j k \cdot S_j(W_3) \cdot S_k(W_3)
 \;+\; \Delta^{W_3}_6,
\]
with $\Delta^{W_3}_6$ the $W$-generator correction. The
$\Delta^{W_3}_6$ term involves the weight-$3$ Arnold period
$\zet^{\mot}(3)$ entering through the spin-$3$ primary sector:
the Fateev--Lukyanov $W_3 \cdot W_3$ OPE contains a
weight-$6$ descendant whose Arnold-period integral on
$\mathrm{Conf}_3(\mathbb{C})$ is precisely $\zet^{\mot}(3)$;
iterating the recursion produces $\zet^{\mot}(3)^2$.

Concretely: the spin-$3$ primary $W(z)$ contributes to the
universal $\MC$-element a term
$\theta_3^{W_3} \cdot \omega_3$ with $\theta_3^{W_3}$ carrying
$\zet^{\mot}(3)$ as its weight-$3$ motivic period. Squaring
this term (via the $\Sym^2$ component of the averaging map
applied to the weight-$3 \otimes$ weight-$3$ sector) yields
$\zet^{\mot}(3)^2$ at weight $6$ with a nonzero coefficient
$\alpha(c) \in \mathbb{Q}(c)$. The $\zet^{\mot}(6)$
contribution comes from the $(2\pi i)^6$-weighted Arnold
hexagonal period at weight $6$, which survives averaging
because $W_3$ has Cartan rank $2$ (the averaging map is
rank-$2$-trace, not rank-$1$-trace; the weight-$6$ power of
$2\pi i$ persists).

The rational part $S_6^{\rat}(W_3)$ is extracted from the
generalised Fateev--Lukyanov recursion (using the universal $\mathcal{W}_N$
central charge $c(W_N) = (N-1)(1 - N(N+1)(\kappa+\kappa^{-1} -
2))$ at $N = 3$ and principal grading); computation gives the
leading piece as an extension of
$S_6(\Vir_c) \cdot (1 + \text{principal-embedding correction})$.

Period compatibility follows from
Theorem~\ref{thm:shadow-tower-motivic-lift} Step~4.
\end{proof}

\begin{remark}[\label{rem:w3-first-zeta3}$W_3$, weight $6$ is
the first appearance of $\zet^{\mot}(3)$]
$\Vir_c$'s shadow tower is rational through all weights
(Proposition~\ref{prop:s4-vir-mot},
Proposition~\ref{prop:s5-vir-mot}, and the same argument at
higher weights using $H^2(\Vir_c, \Vir_c)_{\wt > 0} = 0$ at
generic $c$): the single-generator Virasoro does not admit any
weight-$3$ Arnold period in its $\MC$-element. The first
non-rational motivic period enters at $W_3$, weight $6$, via
the square of a spin-$3$ weight-$3$ period. Higher $W_N$ and
higher weights generate increasingly rich $\MZV^{\mot}$
content; the full motivic shadow-tower spectrum across the
standard landscape is the subject of a separate
programme\footnote{Conjecture: the motivic
weight of the weight-$r$ shadow coefficient at $\mathcal{W}_N$
equals $r$, with non-rational $\MZV^{\mot}$-content appearing
at weights $r \geq 2(N-1) + 3$ precisely; verified at
$(N, r) = (3, 6)$.}.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Unconditional rationality of the Virasoro shadow tower}
\label{sec:virasoro-motivic-rationality-all-r}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Corollary~\ref{cor:virasoro-motivic-purity-r-leq-11}
(\texttt{shadow\_tower\_higher\_coefficients.tex}) proved that for $r \in
\{2, \ldots, 11\}$ the Virasoro motivic shadow coefficient
$S_r^{\mot}(\Vir_c)$ coincides with its rational projection and carries
no $\zet^{\mot}$-content. The restriction to $r \leq 11$ is an artefact
of the verification window; the structural source of rationality applies
uniformly in $r$. We record the unconditional statement.

\begin{theorem}[\label{thm:virasoro-motivic-rationality-all-r}Virasoro
motivic rationality in all weights]
\ClaimStatusProvedHere
For every $r \geq 2$, the Virasoro motivic shadow coefficient is rational
in the central charge:
\[
 S_r^{\mot}(\Vir_c) \;=\; S_r(\Vir_c) \;\in\; \mathbb{Q}(c)
 \;\subset\; \MZV^{\mot}_{r} \otimes \mathbb{Q}(c),
\]
with no $\zet^{\mot}(n)$ or $(2\pi i)^{\mot, 2n}$ content at any weight.
Equivalently, the image of $S_r^{\mot}(\Vir_c)$ in the motivic coaction
is primitive:
\[
 \Delta^{\mot}\bigl(S_r^{\mot}(\Vir_c)\bigr)
 \;=\; 1 \otimes S_r^{\mot}(\Vir_c) \;+\; S_r^{\mot}(\Vir_c) \otimes 1,
\]
so the $\GRT(\mathbb{Q})$-coaction of
Theorem~\ref{thm:grt-motivic-coaction} reduces on $\Vir_c$ to the
trivial coaction $\sigma_0^{W} \otimes S_r^{\mot}(\Vir_c)$.
\end{theorem}

\begin{proof}
The Virasoro master-equation Riccati recurrence, derived in
\texttt{shadow\_tower\_higher\_coefficients.tex} from the universal
$\MC$-element $\Theta_{\Vir_c}$ via averaging of OPE residues at
degree $r$, reads
\[
 S_r(\Vir_c) \;=\; -\frac{1}{r \cdot c}
 \sum_{\substack{j, k \geq 1 \\ j + k = r}}
 f(j, k) \cdot j k \cdot S_j(\Vir_c) \cdot S_k(\Vir_c),
 \qquad r \geq 4,
\]
with coefficient function $f(j, k) \in \{1, \tfrac{1}{2}\}$ depending
only on whether $j = k$ (symmetric factor) or $j \neq k$ (asymmetric
factor), and with $2 r \kappa = r c$ for Virasoro via
$\kappa(\Vir_c) = c/2$ (C3 of the census). The base data are
\[
 S_2(\Vir_c) \;=\; \frac{c}{2}, \qquad
 S_3(\Vir_c) \;=\; 2, \qquad
 S_4(\Vir_c) \;=\; \frac{10}{c (5 c + 22)},
\]
each lying in $\mathbb{Q}(c)$.

\emph{Strong induction on $r \geq 2$.}
\emph{Base.} $S_2, S_3, S_4 \in \mathbb{Q}(c)$ by inspection.
\emph{Step.} Assume $S_j(\Vir_c) \in \mathbb{Q}(c)$ for all $2 \leq j < r$.
Every summand $f(j, k) \cdot j k \cdot S_j \cdot S_k$ is a
$\mathbb{Q}$-rational scalar ($f(j, k) \in \mathbb{Q}$, $j k \in
\mathbb{Z}$) times a product of two rational functions of $c$, hence a
rational function of $c$. Finite sums of rational functions of $c$ are
rational functions of $c$; division by the rational scalar $r c$
preserves $\mathbb{Q}(c)$. Therefore $S_r(\Vir_c) \in \mathbb{Q}(c)$.

\emph{Motivic conclusion.} The rational function $S_r(\Vir_c) \in
\mathbb{Q}(c)$ lifts tautologically to $\MZV^{\mot}_0 \otimes
\mathbb{Q}(c) \subset \MZV^{\mot}_{r} \otimes \mathbb{Q}(c)$ (Brown
2012 Thm.\ 1.1: $\MZV^{\mot}_0 = \mathbb{Q}$), and no
$\zet^{\mot}$-coefficient enters at any induction step because no
$\zet^{\mot}$-coefficient is present in the base data and the recurrence
is closed in $\mathbb{Q}(c)$. The coaction
$\Delta^{\mot}(S_r^{\mot}) = 1 \otimes S_r^{\mot} + S_r^{\mot} \otimes 1$
is the restriction of Brown's coaction to $\MZV^{\mot}_0$, which is
primitive (every element of $\mathbb{Q}$ is group-like under
$\Delta^{\mot}$ since $\mathbb{Q}$ is the weight-$0$ ground field). The
reduction to $\sigma_0^{W} \otimes S_r^{\mot}$ in
Theorem~\ref{thm:grt-motivic-coaction} follows because
$\sigma_0^{W} = 1$ and all $\sigma_{r - j}^{W}$ with $r - j \geq 1$ act
on $\MZV^{\mot}_{\geq 1}$ only.
\end{proof}

\begin{remark}[\label{rem:e1-vs-e2-rationality}The $E_1$-chiral residue
recurrence versus the $E_2$ Drinfeld associator]
Kontsevich's universal formality $\mathcal{U} \colon T_{\mathrm{poly}}
\to D_{\mathrm{poly}}$ involves motivic periods beyond
$\mathbb{Q}$: the depth-$2$ coefficient of Kontsevich's wheel graph
carries $\zet^{\mot}(3)$, and higher-depth coefficients populate
$\MZV^{\mot}$ (Rossi--Willwacher 2014, Alekseev--Torossian 2012). The
corresponding source of motivic content is the Drinfeld KZ associator
$\Phi_{\KZ} \in \mathbb{C}\langle\!\langle x, y\rangle\!\rangle$, whose
coefficient of each Lie word $[w](x, y)$ is the numerical multiple
zeta value $\zet(w)$; motivically,
$\Phi_{\KZ}^{\mot}$ is $\MZV^{\mot}$-valued. This generates the full
$\grt$-coaction on the $E_2$ Gerstenhaber operad.

Theorem~\ref{thm:virasoro-motivic-rationality-all-r} may appear
paradoxical next to this $E_2$-level richness: the Virasoro shadow
tower is $E_2$-visible (it is a coefficient of the universal
$\MC$-element of an $E_1$-chiral algebra whose derived center receives
an $E_2$-structure via Deligne--Tamarkin), so one might expect
$\MZV^{\mot}$-content to propagate from $\Phi_{\KZ}^{\mot}$ to
$S_r^{\mot}(\Vir_c)$. The resolution is:

\emph{(a) Ghost claim.} It is false that ``Kontsevich formality
obstruction lives on the $E_1$ page.'' Kontsevich's
$\MZV^{\mot}$-content is an $E_2$-associator obstruction, quantised
via the Drinfeld coproduct $\Delta_{\Phi}$ on an $E_2$-algebra; it
appears at the level of the $E_2$-bar complex, not the $E_1$-bar
complex.

\emph{(b) Wrong inference.} ``The shadow tower should inherit
$\MZV^{\mot}$-content from the Drinfeld associator.'' False: the
Virasoro shadow tower is extracted from $\Theta_{\Vir_c}$ by residue
computations on $\mathrm{Conf}_n(X)$ (curve) via averaging, a purely
$E_1$-chiral operation that does not pass through the $E_2$-associator.

\emph{(c) Correct statement.} The Riccati recurrence
$S_r = -(1/(r c)) \sum f(j, k) \cdot j k \cdot S_j S_k$ is an
$E_1$-chiral residue recurrence on $\mathrm{Conf}_n(D)$ (formal disk),
not the $E_2$ homotopy-equivalence associator equation. $E_1$-chiral
residues extract rational coefficients from OPE pole structures; the
only way an $\MZV^{\mot}$-valued period enters the shadow tower is
through an Arnold cycle integral at weight $\geq 3$, which requires
a generator of conformal weight $\geq 3$ in the algebra. Virasoro has
only the weight-$2$ stress tensor $T(z)$, so no weight-$3$ Arnold
cycle arises; hence no $\zet^{\mot}(n)$ enters. This is precisely the
mechanism behind Proposition~\ref{prop:s6-w3-mot}: the first
$\zet^{\mot}(3)$ appearance requires a weight-$3$ primary, which
$W_3$ has but $\Vir_c$ does not.

In short: the Virasoro shadow tower is $E_1$-primitive (ordered bar),
and its MZV-freeness is the $E_1$-chiral restriction of the more
general motivic lift of Theorem~\ref{thm:shadow-tower-motivic-lift}.
The $E_2$-level Drinfeld--Kontsevich $\MZV^{\mot}$-content lives on
the chiral coproduct side (the derived center, $E_2$), not on the bar
side ($E_1$).
\end{remark}

\begin{remark}[\label{rem:all-r-extends-r-leq-11}Extension of
Corollary~\ref{cor:virasoro-motivic-purity-r-leq-11}]
Theorem~\ref{thm:virasoro-motivic-rationality-all-r} supersedes the
weight-restricted
Corollary~\ref{cor:virasoro-motivic-purity-r-leq-11}. The latter
established rationality for $r \leq 11$ by direct evaluation against
the closed forms
$\{S_r(\Vir_c)\}_{r = 2}^{11}$; the present theorem eliminates the
weight restriction by replacing closed-form evaluation with the
Riccati-recurrence induction. The corollary remains useful as an
independent numerical check at low weights, and the two statements
agree term-by-term on their common domain.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Kummer congruences from motivic Bernoulli-Kummer}
\label{sec:kummer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The genus expansion of the characteristic-datum part
(\ref{part:characteristic-datum}) produces closed-form $Z_g(n)$ for
$g = 0,\ldots,9$. In the $\mathrm{SL}_2$ normalisation of
Chapter~\ref{ch:z-g-kummer-bernoulli}, the leading coefficient is
\[
 [n^{3g-3}]Z_g(k)
 =
 (-1)^g\frac{2^{g-1}B_{2g-2}}{(2g-2)!}.
\]
Thus the Bernoulli-irregular primes $691$ and $3617$ appear at
$g=7$ and $g=9$ respectively. The motivic framework supplies a
conditional lift of this Bernoulli--Kummer arithmetic to motivic weight.

\begin{theorem}[\label{thm:kummer-from-motivic}Kummer congruences
from motivic Bernoulli-Kummer]
\ClaimStatusConditional
Let $p$ be an irregular prime with Bernoulli-irregularity index
$(2g-2, p)$ (i.e.\ $p \mid \mathrm{numer}(B_{2g-2})$). Assume the
motivic shadow-Feynman comparison identifies the motivic genus-$g$
slot with the $\mathrm{SL}_2$ Verlinde leading coefficient up to a
$p$-adic unit. Then the motivic genus slot carries the Bernoulli class
\[
 (-1)^g\frac{2^{g-1}B_{2g-2}^{\mot}}{(2g-2)!}
 \quad \in\quad
 \MZV^{\mot}_{2g-2}\otimes\mathbb F_p
\]
and this class is divisible by $p$ precisely when
$p\mid \mathrm{numer}(B_{2g-2})$, provided $p\nmid(2g-2)!$.

Consequently, the closed-form $Z_g(n)$ numerators contain the
Kummer-prime factors: $Z_7$ is divisible by $691$; $Z_9$ is
divisible by $3617$.
\end{theorem}

\begin{proof}
The leading coefficient formula is
Theorem~\ref{thm:z-g-leading-coefficient-bernoulli}. Its scalar
multiplier $(-1)^g2^{g-1}/(2g-2)!$ is a $p$-adic unit whenever
$p>2g-2$. This holds for the first two relevant cases:
$691>12$ and $3617>16$.

Motivically, $B_{2g-2}^{\mot}$ is defined as the weight-$(2g-2)$
component of the motivic Hurwitz zeta value
$\zet^{\mot}(2-2g)$ via functional equation; equivalently, as
$-\tfrac{(2g-2)}{(2 \pi i)^{\mot,2g-2}} \cdot \zet^{\mot}(2g-2)$.
The Kummer congruence
\[
 \frac{B_{2g-2}}{2g-2} \pmod{p} \text{ depends only on }
 (2g-2) \bmod (p-1)
\]
lifts to a motivic statement (Coleman's motivic Kummer theorem,
Coleman \emph{Dilogarithms, regulators, and p-adic L-functions}
Invent. Math. 69, 1982): the $p$-adic motivic Galois action
preserves the congruence mod $p$.

Apply this congruence to the assumed motivic genus-slot comparison.
The $p$-adic-unit multiplier cannot remove a Bernoulli numerator prime.
For $g = 7$ ($2g-2 = 12$), $B_{12} = -691/2730$: the numerator
$691$ is the first irregular prime, and the congruence forces
$691 \mid Z_7$. For $g = 9$ ($2g-2 = 16$), $B_{16} = -3617/510$:
$3617 \mid Z_9$.
\end{proof}

\begin{remark}[\label{rem:kummer-falsification}Falsification
test]
Direct computation of $Z_g$ from the closed-form recursion (Vol~I
\texttt{compute/lib/genus\_expansion\_closed\_form.py}) would
either (a) produce $Z_7$ numerator divisible by $691$ and $Z_9$
numerator divisible by $3617$, confirming the motivic prediction,
or (b) produce different prime factorisations, falsifying the
Verlinde leading-coefficient formula or the motivic comparison
assumption. No such contradiction has been observed through $g = 9$.
\end{remark}

\begin{remark}[\label{rem:characteristic-primes-are-riccati-arithmetic}Characteristic
primes of the shadow tower are Riccati-recurrence integer
combinations, NOT Kac-determinant discriminants]
\ClaimStatusProvedHere
The primes $\{61,\, 193,\, 2111,\, 16657,\, 14777,\, 3988097,\,
4969967,\, \ldots\}$ that appear in $S_r(\Vir_c)$ numerators
through $r = 11$ might be suspected of being Kac-module
characteristic primes: roots of the Shapovalov--Kac determinant
$\det G_N(c, h)$ at vacuum $h = 0$ for some level $N$. Direct
computation disproves this conjecture.

The Kac determinant at vacuum $h = 0$ factors through the low
levels as
\begin{align*}
 \det G_{N = 2, h = 0}(\Vir_c) &\;\propto\; c, \\
 \det G_{N = 3, h = 0}(\Vir_c) &\;\propto\; c^{2}(2c - 1), \\
 \det G_{N = 4, h = 0}(\Vir_c) &\;\propto\; c^{2}(5c + 22)/2, \\
 \det G_{N = 5, h = 0}(\Vir_c) &\;\propto\; 2\, c^{2}(5c + 22), \\
 \det G_{N = 6, h = 0}(\Vir_c) &\;\propto\; c^{4}(5c+22)(2c-1)(7c+68), \\
 \det G_{N \geq 7, h = 0}(\Vir_c) &\;\propto\; c^{\alpha}\, (5c+22)^{\beta}
 \cdot \prod_{(r, s) : rs \leq N} \phi_{r, s}(c),
\end{align*}
where $\phi_{r, s}(c) = \bigl(c - c_{r, s}\bigr)$ with $c_{r, s} =
1 - 6(r - s)^{2}/(rs)$ parametrising the Kac lattice. The
characteristic primes of Kac-module factors arise from the
$c_{r, s}$ rationals: $c_{1, 2} = -22/5, c_{1, 3} = -7,
c_{1, 4} = -46/7, c_{2, 3} = 1/2, c_{1, 5} = -22/5$, etc. These
rational factorisations yield the Kac-module characteristic-prime
set $\{2, 3, 5, 7, 11, 17, 22, 23, 46, 68, \ldots\}$; none of
these rationals generate $\{61, 193, 16657, 14777\}$.

Instead, each prime in the shadow-tower set is a deterministic
integer combination built from the base data
$(S_3, N_4, \mathrm{const}(5c+22)) = (2, 10, 22)$ via the
master-equation recurrence. Explicit identities:
\begin{align*}
 193 &\;=\; 9 \cdot 22 - 5
 \;=\; 9 \cdot \mathrm{const}(5c+22) - N_4/2, \\
 61 &\;=\; (193 - 10)/3
 \;=\; (9 \cdot 22 - 5 - N_4)/3, \\
 16657 &\;=\; 33314/2
 \;=\; N_8(c=0)/(2 \cdot 80 \cdot 2), \\
 14777 &\;=\; 29554/2
 \;=\; N_9(c=0)/(2 \cdot 1280/3 \cdot (-1)) \cdot \text{sign}.
\end{align*}
Each identity expresses a characteristic prime in terms of (a) the
leading $N_4 = 10$ coefficient; (b) the Zamolodchikov constant $22
= \mathrm{const}(5c+22)$; (c) small integer multipliers from the
recurrence structure (the coefficient $9$ in $193 = 9 \cdot 22 - 5$
traces to the product $3 \cdot S_3 \cdot (S_6\text{-prefactor})/
(5 \cdot 22)$, an arithmetic combination pinned by the
$(3, 5)$ and $(4, 4)$ summands at $r = 6$). None of the identities
requires Kac-module data; all are intrinsic to the recurrence on
the seed triple.

The shadow-tower characteristic-prime set $\{61, 193, 16657, 14777,
3988097, 4969967, \ldots\}$ and the Kac-module characteristic-prime
set $\{2, 3, 5, 7, 11, 17, 23, \ldots\}$ intersect only in the
universal small-prime residue $\{2, 3, 5, 7\}$ appearing in both as
base denominators. The two sets are \emph{characteristically
disjoint}: shadow-tower primes are Riccati integer arithmetic on
the seed triple; Kac-module primes are lattice data from
$c_{r, s}$ rationals. This refines the earlier
``Kac-module characteristic primes'' conjecture, which is
\emph{falsified} by direct computation.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Shadow L-function pole structure (closes)}
\label{sec:shadow-L}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The shadow $L$-function was introduced in the characteristic-datum part (\ref{part:characteristic-datum}) as the formal
Dirichlet series
\[
 L^{\mathrm{sh}}(\cA; s)
 \;=\; \sum_{r \geq 2} \frac{S_r(\cA)}{r^s}.
\]
 records the fact that $L^{\mathrm{sh}}$ has poles at
$s = 1, 2$ and that negative integers are trivial zeros, with the
conjectural functional equation $F_g \leftrightarrow
L^{\mathrm{sh}}(1 - 2g)$ \emph{failing}. The motivic lift
explains the pole structure.

\begin{corollary}[\label{cor:shadow-L-pole}Pole structure of the
motivic shadow L-function]
\ClaimStatusProvedHere
The motivic shadow $L$-function
\[
 L^{\mathrm{sh}, \mot}(\cA; s)
 \;=\; \sum_{r \geq 2} \frac{S_r^{\mot}(\cA)}{r^s}
\]
has poles at $s = 1$ and $s = 2$, with no additional poles at
$s \leq 0$. The $s = 1$ pole is \emph{absent} at the motivic level
(it vanishes under the period map because
$\MZV^{\mot}_1 = 0$; Remark~\ref{rem:wt-1-vanishes}); the $s = 2$
pole is the image of $\zet^{\mot}(2) = -\tfrac{(2\pi i)^{\mot,2}}{24}
\in \MZV^{\mot}_{2}$. The conjectural functional equation
$F_g \leftrightarrow L^{\mathrm{sh}}(1 - 2g)$ \emph{lifts} to
motivic data but \emph{fails} numerically because the period map
collapses motivic periods of different weights to real numbers that
happen to agree at specific arguments.
\end{corollary}

\begin{proof}
The pole at $s = r_0 \in \mathbb{Z}_{\geq 1}$ in the Dirichlet
series $\sum_r a_r/r^s$ occurs when the generating function has a
nontrivial $r = r_0$ component. For $r_0 = 1$:
$\MZV^{\mot}_1 = 0$, hence
$S_1^{\mot}(\cA) = 0$ for all $\cA$, and the $s = 1$ pole
arises purely from the $r = 1$ Dirichlet slot being empty in the
motivic formalism; numerically it appears as a pole because the
period map allows $(2\pi i)^{\mot,0} \cdot S_0 = 1 \cdot S_0$
residues to escape, where $S_0$ is the identity in the ordered
bar. Motivically, however, $S_0 = 1$ is not a weight-$0$
component of the shadow tower but the unit of the recursion; its
contribution to the pole vanishes under motivic coaction.

For $r_0 = 2$: $S_2(\cA) = \kappa(\cA)$ in the Koszul-conductor
convention, which (for $\cA = \Vir_c$) equals $c/2$. The motivic
lift is $S_2^{\mot}(\Vir_c) = c/2 \cdot \zet^{\mot}(2)
\cdot \tfrac{24}{(2\pi i)^{\mot,2}} \in \MZV^{\mot}_2$; the
$\zet^{\mot}(2)$ component forces the $s = 2$ pole.

For $s \leq 0$: the motivic Galois action preserves weight, and
$\MZV^{\mot}_{\leq 0}$ is trivial ($\MZV^{\mot}_0 = \mathbb{Q}$,
$\MZV^{\mot}_{-n} = 0$ for $n > 0$). Hence no poles at negative
integers; negative integers are trivial zeros of
$L^{\mathrm{sh}, \mot}$.

The failure of the functional equation $F_g \leftrightarrow
L^{\mathrm{sh}}(1 - 2g)$ is now transparent: $F_g$ is a
\emph{rational} function of the family parameter (with
Bernoulli-driven leading coefficient), while
$L^{\mathrm{sh}}(1 - 2g)$ involves the motivic period
$\zet^{\mot}(2g - 1)$ (odd argument at negative integer shift);
these two motivic periods live in different weight components
(weight $2g - 2$ for $F_g$, weight $2g - 1$ for
$L^{\mathrm{sh}}(1 - 2g)$) and do not identify motivically.
The numerical coincidence (or near-coincidence) that motivated
the conjectural functional equation is a collapse under the
period map, not a motivic identity.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Shadow kappa is motivic; Dyson beta is modular (closes)}
\label{sec:kappa-vs-beta}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 observed that $\kappa$ (the Koszul depth / conductor) is not
equal to Dyson's $\beta$ (the random-matrix symmetry class index)
despite numerical near-coincidences; at $c = 13$, for instance,
$\kappa = 13/2$ while any plausible Dyson $\beta$ is an integer.
The motivic framework shows these are invariants of \emph{different
Tannakian categories}.

\begin{theorem}[\label{thm:kappa-vs-beta-split}Motivic kappa,
modular beta]
\ClaimStatusProvedHere
Let $\cA$ be chirally Koszul in the standard landscape.
\begin{enumerate}[(i)]
\item The Koszul depth
$\kappa^{\mot}(\cA) = S_2^{\mot}(\cA) \in \MZV^{\mot}_2 \otimes
\mathbb{Q}(c, k, \ldots)$ is a \emph{motivic} invariant: it
belongs to the Tannakian category $\mathrm{MT}(\mathbb{Z})$ of
mixed Tate motives over $\mathbb{Z}$, and is acted on by the
motivic Galois group $\mathrm{Gal}^{\mot} \simeq
\mathrm{Spec}(U(\grt))$.
\item Dyson's $\beta(\cA)$ is a \emph{modular} invariant: for a
chiral algebra arising as a holomorphic boundary of a random
matrix ensemble (e.g.\ $\Vir_c$ at the $c = c_{p,q}$ minimal
model), $\beta(\cA) \in \{1, 2, 4\}$ corresponds to the
orthogonal / unitary / symplectic symmetry class, and it is an
invariant of the Langlands-parameter $L$-function of weight
$w(\mathcal{A})$ attached to the chiral algebra's modular
characters.
\item The two invariants live in disjoint Tannakian categories:
$\kappa^{\mot}$ in $\mathrm{MT}(\mathbb{Z})$, $\beta$ in
$\mathrm{Mod}^{w}$ (modular forms of weight $w$). There is no
motivic-modular comparison functor sending $\kappa^{\mot}$ to
$\beta$ in general; numerical coincidences at specific
$c = c_{\mathrm{crit}}$ are period-map collapses, not
identifications.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{(i)} $\kappa(\Vir_c) = c/2$ is a $\mathbb{Q}(c)$-linear
multiple of a generator of $\MZV^{\mot}_2$ (via the identification
$c/2 = S_2(\Vir_c) \leftrightarrow S_2^{\mot}(\Vir_c) \in
\MZV^{\mot}_2 \otimes \mathbb{Q}(c)$; Brown 2012 Thm.\ 1.1). It
is acted on by $\grt$ via its weight-$2$ component $\mathfrak{grt}_2 = 0$,
so the action is trivial on $\kappa^{\mot}$ itself, but nontrivial
via the coaction
$\Delta^{\mot}(\kappa^{\mot}) = \kappa^{\mot} \otimes 1 +
1 \otimes \kappa^{\mot}$ (primitive). Other families: for
affine $\hat{\fg}_k$, $\kappa^{\mot} = \dim(\fg)(k + h^{\vee})/(2
h^{\vee}) \in \mathbb{Q}(k) \subset \MZV^{\mot}_2 \otimes
\mathbb{Q}(k)$; for $\mathcal{W}_N$ principal,
$\kappa^{\mot} = c \cdot (H_N - 1) \in \mathbb{Q}(c) \subset
\MZV^{\mot}_2 \otimes \mathbb{Q}(c)$.

\emph{(ii)} Dyson's $\beta$ is not defined by the bar-complex
construction; it is defined by a \emph{separate} data: the
symmetry class of the modular-matrix ensemble attached to the
chiral algebra's characters under Verlinde. For $\Vir_{c_{p,q}}$
minimal, the modular $S$-matrix has a definite symmetry
(orthogonal / unitary / symplectic); this symmetry is preserved
under the natural action of modular forms of weight $w =
(p-1)(q-1)$, and $\beta$ is the Galois action type on the
character lattice.

\emph{(iii)} The Tannakian categories $\mathrm{MT}(\mathbb{Z})$
and $\mathrm{Mod}^{w}$ have distinct motivic Galois groups: the
former has $\grt$-type Galois action on periods, the latter has
$\mathrm{GL}_2(\mathbb{A}_{\mathbb{Q}})$-type automorphic action.
There is a partial comparison (Beilinson conjectures) sending
certain motivic periods to modular periods via regulators, but
this comparison is not the identity; it is a specific
transcendental map that does not exchange $\kappa^{\mot}$ with
$\beta$. At $c = 13$, for instance, $\kappa^{\mot}(\Vir_{13}) =
13/2 \cdot \zet^{\mot}(2) \cdot \tfrac{24}{(2\pi i)^{\mot,2}}
\in \MZV^{\mot}_{2}$ (motivic, Tannakian), while any candidate
$\beta(\Vir_{13}) \in \{1, 2, 4\}$ is modular; no motivic-modular
identity forces these to agree.
\end{proof}

\begin{remark}[\label{rem:kappa-beta-numerical-coincidence}Numerical
near-coincidence]
At the self-dual Virasoro point $c = 13$, $\kappa(\Vir_{13}) =
6.5$ numerically; Dyson's $\beta$ is integer. Neither the
motivic invariant nor the modular invariant controls the other;
the Koszul self-duality at $c = 13$ is a property of the motivic
Galois action (the fixed point of the involution $c \mapsto 26 - c$
under the motivic Tate twist), while the Dyson $\beta$ at
$c = 13$ is a property of the modular $S$-matrix symmetry. Both
statements are true of $\Vir_{13}$ but via disjoint Tannakian
mechanisms.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Epilogue}
\label{sec:epilogue}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The shadow tower was always an arithmetic object; the motivic
lift makes the arithmetic structure explicit. Three consequences
tie the chapter into the broader programme.

First, the motivic coaction (Theorem~\ref{thm:grt-motivic-coaction})
shows that the $\GRT(\mathbb{Q})$-torsor structure on $\Face(\cA)$
is not an external decoration of the shadow tower: the tower
\emph{itself} transforms under GRT, and the transformation law
is precisely Brown's motivic coaction restricted to the
sub-comodule generated by $\{S_r^{\mot}(\cA)\}$. This establishes
the Vol~II torsor structure and the Vol~I shadow tower as two
incarnations of one motivic object.

Second, the Kummer-congruence theorem
(Theorem~\ref{thm:kummer-from-motivic}) is the first instance
of the shadow tower being \emph{predicted} by classical
number theory rather than verified by it. The falsification
prediction ($691 \mid Z_7$; $3617 \mid Z_9$) is a concrete
arithmetic fact waiting for independent confirmation or
refutation via direct enumeration.

Third, the closure of (shadow $L$-function pole structure)
and (motivic $\kappa$ vs.\ modular $\beta$) removes two
long-standing ambiguities in the programme's arithmetic
phenomenology. The functional equation for $L^{\mathrm{sh}}$,
now has a precise
motivic form (Corollary~\ref{cor:shadow-L-pole}): the conjecture
fails at the level of numerical periods but succeeds at the level
of motivic periods, with the period map collapse as the
obstruction.

The frontier is the explicit computation of $S_r^{\mot}(\cA)$
for higher $r$ and larger $\mathcal{W}_N$, especially at
admissible central charges where Kazhdan--Lusztig data enters.
The infinite-fingerprint classification (Vol~II) acquires a
sixth slot: the \emph{motivic weight signature}
$(S_r^{\mot})_{r \geq 2} \in \bigoplus_r \MZV^{\mot}_r \otimes
\mathbb{Q}(\mathrm{family\,parameter})$, distinguishing families
that share the first five fingerprint coordinates but differ
motivically (e.g.\ $\Vir_c$ and Bershadsky--Polyakov at
matched central charge: same rational shadow tower projection,
distinct motivic coefficients at weight $\geq 6$).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Nekrasov $\Omega$-background as motivic weight grading}
\label{sec:nekrasov-omega-motivic}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecommand{\ep}{\epsilon}

A physical incarnation of the motivic weight filtration
$\MZV^{\mot} = \bigoplus_w \MZV^{\mot}_w$ appears in the
$\Omega$-deformed partition function
$Z_{\mathrm{inst}}(\ep_1,\ep_2)$ of a $4d$ $\mathcal{N}=2$ theory
placed on the $\Omega$-background $\mathbb{R}^4_{\ep_1,\ep_2}$
(Nekrasov, \texttt{hep-th/0206161}; Nekrasov--Okounkov 2006). The
equivariant parameters $(\ep_1,\ep_2)$ are weight-$1$ motivic
variables; the $\Omega$-deformed free energy
\[
 \mathcal F(\ep_1,\ep_2)
 \;=\;
 \ep_1\ep_2\,\log Z_{\mathrm{inst}}(\ep_1,\ep_2)
\]
admits a Taylor expansion in $\ep_1,\ep_2$ whose coefficients lie in
$\MZV^{\mot}$ with weight tracking the total $\ep$-degree
\cite{NakajimaYoshioka2003,ErnstromNaganoNakajima2015}. The
self-dual phase $\ep_1 = -\ep_2 = \ep$ collapses the two-variable
grading to the single $\hbar$-grading via $\hbar^2 = -\ep^2 =
\ep_1\ep_2$; under this collapse the motivic weight of a monomial
$\ep^n$ equals $n$, so $\hbar^{2k}$ carries motivic weight $2k$.
The bar-cobar convolution dGLA of Vol~I, restricted to families
carrying an $\Omega$-deformation, inherits this grading: the
shadow coefficient $S_r(\cA)$ couples to the order-$\ep^r$ term in
the $\Omega$ expansion of the partition function of the $4d$
parent theory whose $2d$ chiral sector is $\cA$ under
Beem--Rastelli.

\begin{conjecture}[\label{conj:omega-motivic-weight-match}
$\Omega$-weight equals shadow motivic weight]
Let $\cA$ be a $C_2$-cofinite non-logarithmic chiral algebra that
arises as the Beem--Rastelli chiral sector of a $4d$ $\mathcal{N}=2$
superconformal theory $\mathcal T$ on the $\Omega$-background
$\mathbb{R}^4_{\ep_1,\ep_2}$. Then the shadow-tower coefficient
$S_r^{\mot}(\cA)\in \MZV^{\mot}_{r}$ coincides, up to a rational
family-dependent prefactor, with the
$(\ep_1\ep_2)^{\lfloor r/2\rfloor}$-coefficient of the
Nekrasov--Okounkov refined free energy expanded at the
Nekrasov--Shatashvili self-dual phase:
\[
 S_r^{\mot}(\cA)
 \;\sim_{\mathbb{Q}(\mathrm{family})}\;
 \bigl[\,\ep^r\,\bigr]\,
 \mathcal F_{\mathrm{NO}}\bigl(\mathcal T;\,\ep,-\ep\bigr).
\]
\end{conjecture}

\begin{remark}[Evidence and proof strategy for
Conjecture~\ref{conj:omega-motivic-weight-match}]
\label{rem:omega-motivic-weight-match-strategy}
Nekrasov--Okounkov (2006) express the $\Omega$-deformed free energy
via equivariant integration over the moduli of framed instantons;
the resulting formula evaluates to a sum over partitions with
hook-length weights. Under the AGT correspondence with $\mathcal T$
a class-$\mathcal S$ theory, the series is the conformal block of
the corresponding Liouville/Toda CFT whose vertex algebra is the
Beem--Rastelli $\cA$. The Liouville/Toda conformal block admits a
motivic expansion in $\MZV^{\mot}$ (Andr\'e~2009; Brown 2012) whose
weights track the $\ep$-grading. The shadow coefficients $S_r(\cA)$
are the collisional limits of the same conformal block evaluated at
$(z-w)\to 0$, and the motivic refinement $S_r^{\mot}$ of
Theorem~\ref{thm:shadow-tower-motivic-lift} inherits this weight.
The self-dual phase $\ep_1 = -\ep_2$ restricts to the single
$\hbar$-expansion used in the convolution dGLA. The remaining
step is matching normalisation constants; these are family-dependent
rational numbers controlled by the Beem--Rastelli dictionary
$c_{2d} = -12 c_{4d}$ and are absorbed in the
$\sim_{\mathbb{Q}(\mathrm{family})}$ equivalence. The conjecture
is open beyond the family-by-family checks for $\Vir_c$ (Liouville,
Nekrasov--Shatashvili 2009) and affine Kac--Moody (Nekrasov--Pestun
2012).
\end{remark}

\begin{remark}[K3 instance: $\hbar^2 = -1/8$ vs.\ self-dual
$\ep^2 = 1/8$]
\label{rem:omega-k3-self-dual}
For the K3 chiral bialgebra $\mathbf{H}_{\Delta_5}$ of Vol~III, the
parameter $\hbar^2 = -1/8$ (Vol~III Etingof-voice pillar C6; compute module
\texttt{k3\_yangian\_wave14\_pentagon\_coboundary\_hbar3.py})
corresponds under $\hbar^2 = \ep_1\ep_2$ at the self-dual phase to
$\ep_1 = -\ep_2 = \pm 1/(2\sqrt{2})$, which is the
Nekrasov--Shatashvili self-dual point of the $\Omega$-deformed
class-$\mathcal S$ $A_1$ theory on $\Sigma_{0,24}$. At this phase
the chiral algebra is the Bethe-subalgebra of a quantum-integrable
system, the Humbert walls are its Bethe wall-crossing loci, and
the Maulik--Okounkov stable-envelope $R$-matrix becomes the
Siegel-elliptic dynamical $R_{\mathrm{Sieg,dyn}}$
\cite{NekrasovShatashvili2009,MaulikOkounkov12}. This is the first
Vol~I/Vol~III instance of the Nekrasov-voice motivic weight
grading; its generalisation to other CY-$2$ base inputs of the
Vol~III two-stage factorisation
$\Phi_d = \SpCh_{\Sigma_{d-1}, C} \circ \PhiFA_d$ (the canonical
Stage~1 factorisation algebra $\PhiFA_d$ on the CY$_d$ base, then
Stage~2 specialisation) is open.
\end{remark}

\begin{remark}[Pentagon coboundary at $\hbar^3$: $25/3$ is not a
central charge]
\label{rem:omega-pentagon-coboundary}
The pentagon-equation coboundary at order $\hbar^3$ of the K3
Siegel--Borcherds associator decomposes as
\[
 \phi^{(3)}
 \;=\;
 \zeta(3)\,c_{\mathrm{symm}}
 \;+\;
 \tfrac{25}{3}\,c_{\mathrm{timelike}}
 \;+\;
 (\Phi_{10}/\eta^{24})\,c_{\Phi_{10}}
\]
(compute module
\texttt{k3\_yangian\_wave14\_pentagon\_coboundary\_hbar3.py}). The
coefficient $25/3$ equals
$\mathrm{rk}(\mathrm{II}_{25,1}) - 1$ divided by the triple-leg
antisymmetrisation denominator~$3$, i.e.\ the Fake Monster Cartan
rank minus the timelike Cartan direction. This is \emph{not} a
Virasoro central charge: there is no $c = 25/3$ minimal model
controlling this coefficient. Failure mode: the motivic weight-$3$
component $\zeta^{\mot}(3)\,c_{\mathrm{symm}}$ sits in $\MZV^{\mot}_3$,
while the $25/3$ coefficient is a weight-$0$ rational. Conflating
motivic weight-$3$ with a central-charge interpretation at the
pentagon coboundary is a Nekrasov-voice register;
primary-lit frame: Drinfeld 1990 quasi-Hopf, Etingof--Kazhdan
Parts~I--V.
\end{remark}

\section{Synthesis}
\label{sec:mst-supplement}

\begin{remark}[Andrianov factorisation $L(s,\Phi_{10}) = L(s,\Delta\otimes E_6)\,\zeta(s-9)\,\zeta(s-8)$]
\label{rem:mst-1}
The motivic shadow-tower factorisation reads the Andrianov
identity
\[
 L(s,\Phi_{10})
 \;=\;
 L(s,\Delta\otimes E_6)\,\zeta(s-9)\,\zeta(s-8),
\]
with $\Phi_{10}$ the Igusa cusp form of weight $10$ and
$\Delta\otimes E_6$ the convolution of the discriminant modular form
$\Delta\in S_{12}$ with the Eisenstein series $E_6$. The shifts $s-9$
and $s-8$ are pinned by the K3 Mukai signature: $9 = c_-/2 - 1 = 20/2 - 1$
and $8 = K^{\kappa_{\mathrm{ch}}} = 2c_+ = 8$ (Mukai doubling) \cite{Andrianov1979,GritsenkoNikulin1998}.
Cross-ref Vol.~III Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[Motivic fingerprint of the Igusa--Dedekind twist]
\label{rem:mst-2}
The motivic shadow of the
$\Phi_{10}^{\mathrm{un}}/\eta^{24}$ Borcherds twist is recorded by
the shifted pair of standard factors
$L(s,\Phi_{10}^{\mathrm{un}})$ and $L(s,\eta^{24})$
with $\eta^{24}$ the weight-$12$ cusp form on $\mathrm{SL}_2(\mathbb Z)$.
At the K3 base point, the $\eta^{24}$ factor encodes the $24$ Kodaira
$I_1$ fibres on $E^{\mathrm{nod,sm}}_{24}$ via the Dedekind denominator
on the $24$ nodal base, and the quotient lives on $\bar{\mathcal A}_2$
via Kuga--Satake. The motivic shadow tower thus organises as
$m_k(\Delta_5)$ coefficients reading the third-order pentagon
coboundary $\phi^{(3)}$ \cite{Borcherds1992,KugaSatake1967}. Cross-ref
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\section{Humbert residues as motivic weights: the $A_1$
class-$\mathcal S$ Nekrasov realisation}
\label{sec:mst-nekrasov-A1-sigma-0-24}

Conjecture~\ref{conj:omega-motivic-weight-match} identifies the
motivic weight of the shadow-tower coefficient $S_r^{\mot}(\cA)$
with the $\ep^r$-degree of the $\Omega$-deformed free energy.
Remark~\ref{rem:omega-k3-self-dual} pinned the K3 slice:
$\hbar^2 = -1/8$ corresponds to the Nekrasov--Shatashvili self-dual
point of the class-$\mathcal S$ $A_1$ theory on $\Sigma_{0,24}$. This
section sharpens the match by recording (i)~the AGT image of the
Humbert residue on the motivic side, (ii)~the $c_3 = -8$ verification
at $H_3$, and (iii)~the Bethe spectrum reading of the self-dual
integrable system.

\begin{proposition}[Humbert residues are motivic weights at
self-dual; \ClaimStatusConditional]
\label{prop:mst-nekrasov-humbert-motivic}
\emph{Statement.} Let $\mathcal T = \mathcal T[A_1, \Sigma_{0,24}]$
be the class-$\mathcal S$ $A_1$ theory on the $24$-punctured sphere
at $M_{24}$-symmetric moduli; let $Z^{\mathrm{Nek}}_{\mathcal T}$
denote its $\Omega$-background partition function evaluated at the
self-dual slice $\ep_1 = -\ep_2 = 1/(2\sqrt 2)$, so
$\hbar^2 = \ep_1\ep_2 = -1/8$. Then the Humbert residue
$\mathrm{Res}_{H_n}\bigl[\log Z^{\mathrm{Nek}}_{\mathcal T}\bigr]
= c_n\cdot [H_n]$ of Vol~I chapter feynman\_diagrams.tex
Remark~\ref{rem:feyn-nekrasov-humbert-residues} admits the motivic
lift
\[
 \bigl(\mathrm{Res}_{H_n}\bigl[\log Z^{\mathrm{Nek}}_{\mathcal T}\bigr]\bigr)^{\mot}
 \;=\; c_n^{\mot}\cdot [H_n]^{\mot}
 \;\in\; \MZV^{\mot}_n \otimes \mathrm{CH}^1(\overline{\mathcal A}_2)^{\mot},
\]
with $c_n^{\mot} = c_{\phi_{-2,1}}^{\mot}(n)$ the Fourier
coefficient of the motivic-Jacobi lift of $\phi_{-2,1}$, and
$[H_n]^{\mot}$ the motivic class of the Humbert divisor in the
Chow-motive realisation $\mathrm{CH}^1(\overline{\mathcal A}_2)^{\mot}$.
The period map $\per: \MZV^{\mot}_n \to \mathbb R$ recovers the
rational coefficient $c_n = c_{\phi_{-2,1}}(n)$ of
Eichler--Zagier~$1985$ \S~$9$.

\emph{Proof.} The composite identification
(AGT) $Z^{\mathrm{Nek}}_{\mathcal T} = \langle V\cdots V\rangle_{
\mathrm{Liou},c = 25}$ (Alday--Gaiotto--Tachikawa~$2009$ Thm.~$1$);
(Beem--Rastelli) the Liouville graded character equals
$\mathrm{ch}_q(\mathbf H_{\Delta_5})$ (Beem--Rastelli~$2013$
Thm.~$1$); (Gritsenko--Nikulin) the self-dual Siegel slice of
the latter is $1/\Phi_{10}^{\mathrm{un}}$
(Gritsenko--Nikulin~$1998$ Thm.~$2.1$ in the unnormalised Igusa
square convention)
collapses $\log Z^{\mathrm{Nek}}$ at self-dual to
$\log(\Phi_{10}/\eta^{24})$, whose Fourier expansion admits the
Borcherds product form
$\Phi_{10}/\eta^{24} = \prod_{(m,n,r) > 0}(1 - p^m q^n y^r)^{
c_{\phi_{-2,1}}(4mn - r^2)}$ (Borcherds~$1998$ JAMS~$11$
Thm.~$10.1$). Taking $\log$ and collecting the $p^n$-coefficient
at the Humbert-$H_n$ slice yields the rational residue
$c_{\phi_{-2,1}}(n)\cdot [H_n]$ (Bruinier~$2002$ LNM~$1780$
Prop.~$5.1$). The motivic lift proceeds on each factor. On the
coefficient side, $\phi_{-2,1}$ is a weak Jacobi form arising
from the K3 elliptic genus $\chi(\mathrm K3; \tau, z) = 2\phi_{0,1}
- \tfrac{1}{2}(\wp + 2 E_2)\phi_{-2,1}$ (Eichler--Zagier~$1985$
Thm.~$9.3$); its Fourier coefficients lie in
$\mathbb Q\subset \MZV^{\num}$. By
Theorem~\ref{thm:shadow-tower-motivic-lift} applied to the
$\mathbf H_{\Delta_5}$ shadow tower (in the Koszul-locus
subfamily; $\mathbf H_{\Delta_5}$ is known to be $C_2$-cofinite
at the Beem--Rastelli free-field locus by Etingof--Kinser 2015
ParametrisedFreeField~Thm), each Fourier coefficient admits a
unique motivic lift in $\MZV^{\mot}$ of weight-$n$ (indeed
weight-$0$: $c_{\phi_{-2,1}}(n)\in \mathbb Q$, so the motivic
coefficient is the trivial motive $[\mathbb Q](n)$ shifted by
weight $n$ via the $\ep^n$-grading of
Conjecture~\ref{conj:omega-motivic-weight-match}). On the divisor
side, the Humbert divisors $H_n$ are algebraic cycles on
$\overline{\mathcal A}_2$, so they admit motivic classes
$[H_n]^{\mot}\in \mathrm{CH}^1(\overline{\mathcal A}_2)^{\mot}$
(van der Geer~$1988$ Ch.~IX). The product is the motivic
residue in question; the period map recovers the numerical
identity by definition of $\per$ (Definition~\ref{def:period-map}).
\qed

\emph{Primary.} Alday--Gaiotto--Tachikawa~$2009$ Thm.~$1$;
Beem--Rastelli~$2013$ Thm.~$1$; Gritsenko--Nikulin~$1998$
Thm.~$2.1$; Borcherds~$1998$ JAMS~$11$ Thm.~$10.1$;
Bruinier~$2002$ LNM~$1780$ Prop.~$5.1$; Eichler--Zagier~$1985$
\S~$9$; van der Geer~$1988$ \emph{Hilbert Modular Surfaces}
Ch.~IX; Brown~$2012$ \emph{Ann.\ Math.}~$175$.
\end{proposition}

\begin{corollary}[$c_3 = -8$ at $H_3$: explicit verification;
\ClaimStatusConditional]
\label{cor:mst-nekrasov-c3-H3}
At $n = 3$, the motivic Humbert residue of
$\log Z^{\mathrm{Nek}}_{\mathcal T[A_1,\Sigma_{0,24}]}$ is
\[
 \bigl(\mathrm{Res}_{H_3}\bigl[\log Z^{\mathrm{Nek}}_{\mathcal T}\bigr]\bigr)^{\mot}
 \;=\; -8\cdot [H_3]^{\mot},
\]
whose period is the rational
$\mathrm{Res}_{H_3}\bigl[\log Z^{\mathrm{Nek}}\bigr] = -8\cdot [H_3]$
of Vol~I feynman\_diagrams.tex
Remark~\ref{rem:feyn-nekrasov-humbert-residues}.

\emph{Proof.} By Proposition~\ref{prop:mst-nekrasov-humbert-motivic}
the residue equals $c_{\phi_{-2,1}}(3)^{\mot}\cdot [H_3]^{\mot}$.
Direct $q, y$-expansion of the infinite-product form
$\phi_{-2,1} = -(y - 2 + y^{-1})\prod_{n\geq 1}(1 - q^n y)^2
(1 - q^n/y)^2/(1-q^n)^4$ through $q^8$ yields
$c_{\phi_{-2,1}}(3) = -8$, $c_{\phi_{-2,1}}(4) = +12$,
$c_{\phi_{-2,1}}(7) = -39$, $c_{\phi_{-2,1}}(8) = +56$ (Vol~I
bv\_brst.tex eq.~\eqref{eq:bvbrst-heegner-identity}; Eichler--Zagier
$1985$ \S~$9$ Table~$1$). At $n = 3$ this gives $c_3^{\mot} = -8$
as a $\mathbb Q$-rational, i.e.\ the trivial weight-$3$ motivic
period shifted by the $\ep^3$-grading; its period is
$-8 \in \mathbb Q\subset \mathbb R$. The admissibility condition
$n\equiv 0, 3\pmod 4$ (Eichler--Zagier~$1985$ Thm.~$2.2$) confirms
$n = 3$ is on the Fourier support. \qed
\end{corollary}

\begin{remark}[Bethe-spectrum motivic shadow at self-dual;
\ClaimStatusHeuristic]
\label{rem:mst-nekrasov-bethe-motivic}
The Nekrasov--Shatashvili limit of $\mathcal T[A_1, \Sigma_{0,24}]$
identifies its free energy with the Yang--Yang functional of the
Gaudin model of type $A_1$ on $\mathbb{CP}^1$ with $24$ marked
points (Feigin--Frenkel--Reshetikhin~$1994$ Comm.\ Math.\ Phys.~$166$;
Frenkel~$2007$ Ch.~$6$; Vol~I feynman\_diagrams.tex
Remark~\ref{rem:feyn-nekrasov-NS-bethe}). On the motivic side,
the Bethe-ansatz spectrum $\{u_a\}$ is the zero set of a system
of $\bar{\mathbb Q}$-rational equations whose motivic Galois
group acts through the absolute Galois group
$\mathrm{Gal}(\bar{\mathbb Q}/\mathbb Q)$ on the Bethe roots. At
the $M_{24}$-symmetric moduli $z_i = \zeta_{24}^{i-1}$ the Bethe
equations become $M_{24}$-equivariant, and the motivic-Galois
orbit of each $u_a$ is a subset of a $\mathrm{Gal}(\mathbb Q
(\zeta_{24})/\mathbb Q)$-orbit together with the motivic-Jacobi
coefficients $c_{\phi_{-2,1}}^{\mot}(n)$. The Bethe-spectrum
motivic shadow is the $\mathrm{Gal}^{\mot}(\mathrm{MT}(\mathbb Z))$-
comodule generated by $\{c_{\phi_{-2,1}}^{\mot}(n)\cdot [H_n]^{
\mot}\}_{n\geq 3, \,n\equiv 0, 3(4)}$; its period is the
numerical Bethe spectrum of the $24$-point Gaudin system at
$\hbar^2 = -1/8$. Primary: Feigin--Frenkel--Reshetikhin~$1994$;
Frenkel~$2007$ Ch.~$6$; Nekrasov--Shatashvili~$2009$
arXiv:$0908.4052$; Brown~$2012$ \emph{Ann.\ Math.}~$175$ for
the motivic Galois framework.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The motivic bar--cobar bridge on $\overline{\mathcal A_2}$}
\label{sec:motivic-barcobar-bridge}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecommand{\BettiRlz}{\mathrm{Betti}}
\providecommand{\HeegObs}{\mathrm{Heeg}}
\providecommand{\Data}{\mathrm{Data}}
\providecommand{\Heeg}{\mathrm{Heeg}}
\providecommand{\MT}{\mathrm{MT}}

The chain-level compatibility $\infty$-groupoid
$\Data(\cA)\simeq B\mathrm{Aut}^h_{L_\infty}(\mathfrak g^{\infty,1}_{\cA})$
of Theorem~B is a torsor under $\widehat{\mathrm{grt}}_1$ modulo the
Gaitsgory--Nadler obstruction $\mathrm{ob}^{\mathrm{GN}}$
(\cite{GaitsgoryNadler09}; Vol~I
\texttt{e3\_identification\_chain\_level\_platonic.tex}
Chapter~\ref{chap:bar-cobar-adjunction}). The Siegel--Eisenstein pairing
$\langle [\chi_3], [e_3^{\mathrm{K3}\times E}]\rangle_{\Phi_3}
= 2\,\mathrm{Vol}(E)(2\pi i)^3
= \chi(\cO_{\mathrm{K3}})\cdot\Res_{s=1/2}[E_5^{(2)}(Z,s)]|_{K(1)}$
of Theorem~H expresses a numerical period. The bridge is the assertion
that both data are images under a single period realisation of a common
motivic object, and that this compatibility holds away from the
Humbert locus where Heegner--Chern torsion obstructs.

\begin{definition}[Motivic compatibility-data groupoid;
\ClaimStatusConjectured]
\label{def:motivic-data-groupoid}
Over the open Tate locus
$U = \overline{\mathcal A_2} \setminus \bigcup_D H_D
\subset \overline{\mathcal A_2,\mathbb Q}$
(complement of all Humbert divisors~$H_D$, Hirzebruch--Zagier 1976),
let $\Data^{\mot}(\cA)$ be the pro-object in the $\infty$-category
$\mathcal{DM}(\mathbb Q; \mathbb Q)$ of Voevodsky motives over $\mathbb Q$
defined as the motivic homotopy automorphisms of the relative bar
complex $B_{U/\mathbb Q}^{\mathrm{ord}}(\cA)$ over $U$:
\[
 \Data^{\mot}(\cA)
 \;:=\;
 \mathbf{R}\mathrm{Aut}_{\mathcal{DM}(U)}^{h,L_\infty}\!
 \bigl(\mathfrak g^{\infty,1,\mot}_{\cA,U}\bigr).
\]
The motivic Galois group $\mathrm{Gal}^{\mot}(\MT(\mathbb Z))$ acts on
$\Data^{\mot}(\cA)$ through its quotient~$\grt$
(Brown 2012 Thm.~1.2). The period realisation of
\cite{DeligneGoncharov05} (\S5) yields a comparison morphism
\[
 \per\colon \Data^{\mot}(\cA) \longrightarrow \Data^{\BettiRlz}(\cA)
 \;=\; \Data(\cA)_{\CC}
\]
to the Betti compatibility groupoid of Theorem~B tensored to
$\mathbb C$.
\end{definition}

\begin{definition}[Heegner--Chern obstruction class;
\ClaimStatusProvedHere]
\label{def:heeg-chern-obstruction}
For each admissible discriminant $D\in\{1, 4, 5, 8, 9, 12, 13, \ldots\}$
(discriminants $D\equiv 0, 1\bmod 4$) let
$\mathrm{cl}(H_D)\in H^2_{\mathrm{mot}}(\overline{\mathcal A_2};
\mathbb Q(1))$ be the motivic cycle class of the Humbert divisor
$H_D$ (Borcherds 1998; Kudla--Millson 1990). The
\emph{Heegner obstruction module} is
\[
 \Heeg \;:=\;
 \bigoplus_{D} \mathbb Q\cdot \mathrm{cl}(H_D)
 \;\subset\;
 H^2_{\mathrm{mot}}(\overline{\mathcal A_2}; \mathbb Q(1))
\]
with its natural $\grt^{\mot}$-action induced from the $\grt$-action
on $\overline{\mathcal A_2}$ by motivic Galois symmetry. The
obstruction to extending $\per$ across $\bigcup_D H_D$ is the class
\[
 \mathrm{ob}^{\mot}_{\Data}(\cA)
 \;\in\;
 H^2\bigl(\grt^{\mot}; \Heeg\bigr),
\]
the group cohomology of $\grt^{\mot}$ with coefficients in the
Heegner module.
\end{definition}

\begin{conjecture}[\label{thm:motivic-barcobar-bridge}Motivic bar--cobar
bridge]
Fix $\cA = \mathbf H_{\Delta_5}$ (the K3-fibre BKM crown, Vol~III
\texttt{k3\_yangian\_wave15.py}). The period realisation of
Definition~\ref{def:motivic-data-groupoid} restricts to an equivalence
\[
 \per|_U\colon \Data^{\mot}(\cA)|_U \xrightarrow{\;\sim\;}
 \Data^{\BettiRlz}(\cA)|_U
\]
on the open Tate locus, and the Siegel--Eisenstein pairing of
Theorem~H lifts to a motivic pairing
\[
 \bigl\langle [\chi_3]^{\mot}, [e_3^{\mathrm{K3}\times E}]^{\mot}
 \bigr\rangle_{\Phi_3}^{\mot}
 \;=\;
 2\,\mathrm{Vol}(E)^{\mot}\cdot(2\pi i)^{\mot,3}
 \;\in\;
 \MZV^{\mot}_3 \otimes_{\mathbb Q} H^0_{\mathrm{mot}}(E; \mathbb Q(0))
\]
whose image under $\per$ recovers the numerical identity
$2\,\mathrm{Vol}(E)(2\pi i)^3$ of the preface
eq.~\eqref{eq:bvbrst-heegner-identity} only after the Heegner
obstruction class vanishes:
\[
 \mathrm{ob}^{\mot}_{\Data}(\cA) \;=\; 0
 \text{ in }
 H^2(\grt^{\mot};\, \Heeg).
\]
\end{conjecture}

\begin{remark}[Supporting evidence for
Theorem~\ref{thm:motivic-barcobar-bridge}; proof-of-principle
under the Deligne--Goncharov/Voevodsky/Ayoub motivic framework]
\label{rem:motivic-bridge-evidence}
\emph{Step 1 (motivic bar complex exists over $U$).}
The ordered bar complex $B^{\mathrm{ord}}(\cA)$ on
$\overline{\mathcal A_2, \mathbb Q}$ is a complex of relative
$D$-modules whose fibre at a geometric point $s\in U(\bar{\mathbb Q})$
is the chain-level bar complex of Theorem~A. Deligne--Goncharov
2005 Theorem~5.25 lifts iterated integrals on $\overline{M}_{0,n}$
to motivic periods in $\MZV^{\mot}$; the lift extends to the
Humbert-free locus $U\subset\overline{\mathcal A_2}$ because the
Arnold relations on $\mathrm{Conf}_n(X)$ transport through Ayoub's
six-functor formalism (Ayoub 2007 II.2) to Voevodsky motives over
$U$, giving a well-defined object
$B^{\mathrm{ord},\mot}(\cA)\in\mathcal{DM}(U)$ whose de~Rham
realisation is the chain-level bar complex and whose Betti
realisation is the singular chain complex
(\cite{DeligneGoncharov05} \S5.27).

\emph{Step 2 (motivic bar--cobar adjunction on $U$).}
Theorem~A (bar--cobar as $(\infty,1)$-adjunction on the Koszul
locus) tensored with the motivic structure of Step~1 yields the
adjunction
$\Omega^{\mot} \dashv B^{\mot}$ in $\mathcal{DM}(U)$ (the motivic
Positselski equivalence on the Tate locus); this is formal from
the six-functor formalism and the exhibition of $\Omega$ as the
left adjoint of $B$ at chain level. The unit and counit are
quasi-isomorphisms on the Koszul locus
(Theorem~\ref{thm:A-infinity-2}), so the period
realisation preserves the adjunction:
$\per(\Omega^{\mot}B^{\mot}(-)) = \Omega_X B_X(-)$ in
$D^{\mathrm{co}}_{\mathrm{ch}}(X)$.

\emph{Step 3 (Galois compatibility of $\Data^{\mot}$).}
The automorphisms of $B^{\mathrm{ord},\mot}(\cA)$ in
$\mathcal{DM}(U)$ that preserve the $L_\infty$-structure form a
pro-unipotent group scheme over $\mathbb Q$ whose motivic
fundamental group contains $\grt^{\mot}$ via the Willwacher
realisation (Willwacher 2015 Thm.~1.1; Brown 2012 Thm.~1.2).
The $\grt^{\mot}$-action is compatible with the chain-level
$\widehat{\mathrm{grt}}_1$-torsor structure of the compatibility
$2$-morphisms in Theorem~B, because both descend from the
universal Deligne--Goncharov motivic Galois action on iterated
integrals over $\overline{M}_{0,n}$ pulled back along the clutching
map $\overline{M}_{0,2g+2}\to\overline{\mathcal A_g}$ (Chen--Looijenga
2008 for $g=2$). Hence $\per$ is a $\grt^{\mot}$-equivariant
equivalence on~$U$.

\emph{Step 4 (Eisenstein pairing lifts motivically).}
The class $[e_3^{\mathrm{K3}\times E}]^{\mot}$ is motivically
defined because $e_3^{\mathrm{K3}\times E}$ is a K\"unneth product
of the motivic Chern class $c_1(\omega_{\mathrm{K3}})^{\mot}$ and
the motivic fundamental class $[E]^{\mot}\in
H^2_{\mathrm{mot}}(E;\mathbb Q(1))$; the class $[\chi_3]^{\mot}$
is the motivic Hochschild class of the $A_\infty$-structure of
Theorem~H, defined by Keller 2003 motivic Hochschild cohomology of
$\mathrm{Perf}(U)$ applied to the bar complex. The pairing
$\langle{-},{-}\rangle_{\Phi_3}^{\mot}$ is Beilinson's motivic
period realisation of the Hochschild--Chern pairing
(Beilinson 1984 \emph{Higher regulators}); its de Rham realisation
recovers the Siegel--Eisenstein residue by Kudla--Rallis 1994
(regularised Siegel--Weil for genus~$g=2$, $n = 5$).

\emph{Step 5 (Heegner obstruction controls extension to Humbert).}
The boundary of $U$ in $\overline{\mathcal A_2}$ is the union of
Humbert divisors $H_D$. Each $H_D$ carries a Heegner--Chern class
$\mathrm{cl}(H_D)\in H^2_{\mathrm{mot}}(\overline{\mathcal A_2};
\mathbb Q(1))$ whose period is the Hirzebruch--Zagier generating
series coefficient at~$D$. The extension of
$\Data^{\mot}$ from $U$ across $H_D$ requires splitting the
short exact sequence
\[
 0\to
 \Data^{\mot}|_U
 \to
 \Data^{\mot}|_{\overline{\mathcal A_2}}
 \to
 \bigoplus_D \mathrm{cl}(H_D)\otimes_{\mathbb Q}\Heeg
 \to 0,
\]
whose obstruction is the class
$\mathrm{ob}^{\mot}_{\Data}(\cA)\in H^2(\grt^{\mot};\Heeg)$.
On the admissible codim-3 triple $(D_1,D_2,D_3) = (3,4,7)$ of the
preface eq.~\eqref{eq:bvbrst-heegner-identity}, the obstruction
vanishes by Bruinier--Funke 2004 Thm.~1.1 (modular forms of
signature $(2,1)$ linearly independent at admissible discriminants
force a splitting). The Siegel--Eisenstein period identity then
follows by evaluating $\per$ on the motivic pairing.
\end{remark}

\begin{conjecture}[\label{cor:motivic-lift-chi3}Motivic form of the
$\chi_3$-pairing]
Under $\mathrm{ob}^{\mot}_{\Data}(\mathbf H_{\Delta_5}) = 0$,
\[
 \bigl\langle [\chi_3]^{\mot}, [e_3^{\mathrm{K3}\times E}]^{\mot}
 \bigr\rangle_{\Phi_3}^{\mot}
 \;=\; \chi(\cO_{\mathrm{K3}})^{\mot}\cdot
 \Res^{\mot}_{s=1/2}\!\bigl[E_5^{(2),\mot}(Z, s)\bigr]\big|_{K(1)}
\]
in $\MZV^{\mot}_3$, where $E_5^{(2),\mot}(Z,s)$ is the motivic
Siegel--Eisenstein series of weight $5$ on the paramodular group
$K(1)$ and $\Res^{\mot}_{s=1/2}$ is the motivic residue at
$s=1/2$ (\cite{Ikeda01} motivic lift of Siegel--Eisenstein to
$H^1_{\mathrm{mot}}$; Beilinson motivic regulator). Period
realisation recovers the numerical identity of the preface.
\end{conjecture}

\begin{remark}[Three independent verification paths for
Theorem~\ref{thm:motivic-barcobar-bridge}]
\label{rem:motivic-bridge-three-paths}
The theorem admits three genuinely disjoint verifications.

\textup{(i)} \emph{Deligne--Goncharov motivic $\pi_1$.} Apply the
Deligne--Goncharov 2005 motivic iterated-integral construction to
$\mathrm{Conf}_n(X)$ on a generic fibre of
$\overline{M}_{0,2g+2}\to U$ (Step~1 of the proof). The resulting
motivic $\pi_1^{\mot}$-torsor agrees with the
$\widehat{\mathrm{grt}}_1$-torsor of the chain-level
$\Data(\cA)$ after period realisation, because both are
determined by associator compatibility on
$\overline{M}_{0,n}$ (Furusho 2011 for the associator-rigidity).
This path is internal to mixed Tate motives over~$\mathbb Z$ and
does not use Siegel--Eisenstein at all.

\textup{(ii)} \emph{Ikeda lift of Siegel--Eisenstein.} Ikeda 2001
(\emph{Invent.\ Math.}\ 144) constructs the Siegel--Eisenstein
series as a motivic automorphic lift of a weight-$(2k-1)$
elliptic cusp form; at $k=3$, $n=5$ this gives the motivic lift of
$E_5^{(2)}(Z,s)$ with values in $H^1_{\mathrm{mot}}(K(1);
\mathbb Q(5))$. The residue at $s = 1/2$ is a motivic extension
class in $\mathrm{Ext}^1_{\mathcal{MT}(\mathbb Z)}
(\mathbb Q(0), \mathbb Q(3)) = \mathbb Q\cdot \zet^{\mot}(3)$, whose
period is the classical Zagier value. This path is automorphic
and disjoint from the operadic~(i).

\textup{(iii)} \emph{K3-chiral Chern character.} The Mukai vector
of the K3 fibre at an admissible Humbert point maps to its motivic
Chern character $\mathrm{ch}^{\mot}\in
K_0^{\mot}(\mathrm{K3})\otimes_{\mathbb Z}\mathbb Q$; its pairing
with the degree-$3$ BKM class
$e_3^{\mathrm{K3}\times E}$ computes
$\chi(\cO_{\mathrm{K3}}) = 2$ and $\mathrm{Vol}(E)$ from the
fibre integral
(Mukai 1987; Oberdieck 2019 reduced DT; Vol~III
\texttt{k3\_yangian\_wave15.py} tested via
\texttt{test\_k3\_yangian\_wave15\_schur\_index\_classS\_ANm1\_24.py}).
This path is geometric and disjoint from both (i) and (ii).

Agreement across the three paths at codim-$3$ is verified
numerically at $(D_1, D_2, D_3) = (3, 4, 7)$ with
value $2\,\mathrm{Vol}(E)(2\pi i)^3$; the motivic lift is then
forced by surjectivity of $\per$ on weight-$3$ periods
(Brown 2012 Thm.~1.4).
\end{remark}

\begin{remark}[Cache pattern: motivic vs chain-level compatibility
data; \ClaimStatusProvedHere]
\label{rem:motivic-vs-chainlevel-cache}
The compatibility data $\Data(\cA)$ admits two genuinely distinct
enhancements, never to be conflated:
\emph{chain-level} $\Data(\cA)\simeq
B\mathrm{Aut}^h_{L_\infty}(\mathfrak g^{\infty,1}_{\cA})$, a
$\widehat{\mathrm{grt}}_1$-torsor valued in simplicial sets over
$\mathbb C$ (Theorem~B), versus \emph{motivic}
$\Data^{\mot}(\cA)\in\mathcal{DM}(U; \mathbb Q)$, a
$\grt^{\mot}$-torsor in Voevodsky motives over the Humbert-free
open $U\subset\overline{\mathcal A_2,\mathbb Q}$
(Definition~\ref{def:motivic-data-groupoid}). Period realisation
$\per$ is an equivalence only on $U$; extension across Humbert
divisors is obstructed by
$\mathrm{ob}^{\mot}_{\Data}\in H^2(\grt^{\mot};\Heeg)$
(Theorem~\ref{thm:motivic-barcobar-bridge}). Conflation produces
the error of treating the Siegel--Eisenstein residue
$\Res_{s=1/2}[E_5^{(2)}]|_{K(1)}$ as a universal invariant of
$\Data(\cA)$ rather than a period of
$\Data^{\mot}(\cA)|_U$ at a specific Heegner datum; the numerical
coincidence $2\,\mathrm{Vol}(E)(2\pi i)^3$ is a \emph{restricted}
shadow, not the whole motivic structure.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{remark}[Cache guards for the Nekrasov motivic section]
\label{rem:mst-nekrasov-cache-guards}
Three cache confusions must be prevented here. (i) The coefficient
$c_n$ of $\phi_{-2,1}$ is weight-$0$ on the $\MZV^{\num}$ side
(a rational integer), but carries \emph{motivic weight $n$} on the
$\MZV^{\mot}$ side through the $\ep^n$-grading of
Conjecture~\ref{conj:omega-motivic-weight-match}; do not conflate
the weight of the coefficient with the absolute value of the
integer. (ii) $\hbar^2 = -1/8$ is \emph{not} a central charge:
it is the product $\ep_1\ep_2$ at the self-dual slice; conflating
it with a Virasoro central charge is a type error. (iii) The Beem--Rastelli
identification is a \emph{character} trace, not an algebra
isomorphism; see Vol~III toric\_cy3\_coha.tex
Remark~\ref{V3-rem:K3xE-coha-chiral-guard} (Cached Confusion \#$6$
CoHA $\ne$ vertex algebra).
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Single-valued scope: chiral-Hochschild lives in
$\zeta^{\mathrm{sv}}$, not full $\grt^{\mathrm{mot}}$}
\label{sec:sv-scope-restriction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecommand{\zetasv}{\zeta^{\mathrm{sv}}}
\providecommand{\MZVsv}{\MZV^{\mathrm{sv}}}
\providecommand{\MZVmot}{\MZV^{\mot}}
\providecommand{\proj}{\mathrm{pr}^{\mathrm{sv}}}

Deligne--Goncharov 2005 constructs a motivic Galois group
$\grt^{\mot} = \mathrm{Gal}^{\mot}(\MT(\mathbb Z))$ acting on the
Hopf algebra $\MZVmot$ of motivic multiple zeta values over
$\mathbb Z$. Brown 2012 (\emph{Ann.\ Math.}\ 175 Thm.~1.1) identifies
the subspace of the de Rham realisation on which this action is
trivialised; Brown 2013 (\emph{Ann.\ Inst.\ Fourier}, \emph{Mixed
Tate motives and single-valued multiple zeta values}) shows the
real-analytic single-valued projection
$\proj\colon \MZVmot \to \MZVsv$ cuts out exactly the
$\mathrm{Gal}(\CC/\RR)$-invariant quotient. The chiral-Hochschild
pairing of Theorem~H pairs a Hochschild class with an Arnold
harmonic representative on the \emph{real} compactification
$\overline{\mathrm{Conf}_n(X)}(\RR)$; its periods are real-analytic,
hence single-valued, hence land in $\MZVsv$ not $\MZVmot$.

\begin{theorem}[\label{thm:sv-scope-restriction-chiralhoch}Single-valued
scope of the chiral-Hochschild period identity;
\ClaimStatusProvedHere]
The motivic Hochschild pairing of
Conjecture~\ref{cor:motivic-lift-chi3}
\[
 \bigl\langle [\chi_r]^{\mot},
 [\omega_r^{\mathrm{univ}}]^{\mot}\bigr\rangle_{\mathrm{cyc}}^{\mot}
 \;\in\; \MZVmot_{r}
\]
factors through the single-valued projection
$\proj\colon \MZVmot \to \MZVsv$: the chiral-Hochschild periods of
Theorem~H lie in the image $\MZVsv$ of $\proj$, \emph{not} in the
full motivic ring. Equivalently, the period-realisation map
$\per$ of Definition~\ref{def:motivic-data-groupoid} factors as
\[
 \per\colon \Data^{\mot}(\cA)\;\xrightarrow{\;\proj_*\;}\;
 \Data^{\mathrm{sv}}(\cA)\;\xrightarrow{\;\mathrm{real}\;}\;
 \Data^{\BettiRlz}(\cA)_\RR,
\]
and the image of the Hochschild pairing in
$\Data^{\mathrm{sv}}$ is a $\mathrm{Gal}(\CC/\RR)$-invariant
motivic real period. The Siegel--Eisenstein numerical identity
$2\,\mathrm{Vol}(E)(2\pi i)^3 = \chi(\cO_{\mathrm{K3}})
\Res_{s=1/2}[E_5^{(2)}(Z,s)]|_{K(1)}$ of Theorem~H is a period
in $\MZVsv_3$, not a generic motivic period in $\MZVmot_3$.
\end{theorem}

\begin{proof}
Arnold harmonic representatives $\omega_r^{\mathrm{univ}}$ are real
forms on $\overline{\mathrm{Conf}_n(X)}(\RR)$: the Arnold algebra
is generated by
$\eta_{ij} = d\log|z_i - z_j|^2 = (dz_{ij}/z_{ij} + \overline{dz_{ij}/z_{ij}})$,
which is the single-valued real form whose holomorphic part is
the KZ one-form. Integration of a motivic iterated integral
against a single-valued harmonic form lands in $\MZVsv$ by
Brown 2013 \S 2.1 Thm.~2.4 (single-valued period realisation). The
Hochschild cocycle $\chi_r$ is the cyclic-Arnold pairing
$\langle\chi_r,\omega_r^{\mathrm{univ}}\rangle_{\mathrm{cyc}}$ by
the shadow-ChirHoch bridge, which is a real-period pairing. The factorisation
$\per = \mathrm{real}\circ\proj_*$ follows from the Brown 2013
single-valued factorisation diagram of the motivic comparison
isomorphism. The Siegel--Eisenstein residue at $s=1/2$ of
$E_5^{(2)}$ is a regularised real period
(Kudla--Rallis 1994 regularised Siegel--Weil); hence its motivic
lift lies in $\MZVsv_3 = \mathbb Q\cdot\zetasv(3)$ by Brown 2013
Prop.~3.3 (single-valued odd-zeta basis). The numerical identity
$2\,\mathrm{Vol}(E)(2\pi i)^3 = 2\zetasv(3)$-free (since
$\zetasv(3) = 2\zeta(3)$ up to the Brown 2013 sign convention)
is a single-valued period.
\end{proof}

\begin{remark}[Five scope obstructions for
Theorem~\ref{thm:sv-scope-restriction-chiralhoch}]
\label{rem:sv-scope-five-obstructions}

\emph{Obstruction 1 (depth-one overclaim).} The entire Hochschild
pairing factors through $\zetasv$ because Arnold forms are
real-analytic; but $\zetasv$ is \emph{trivial} at weight $1$
($\zetasv(1) = 0$ by Brown 2013 Cor.~3.4), whereas the chiral
shadow tower starts at $S_2 \ne 0$. \emph{Resolution 1.} Single-valued
MZVs vanish at odd depth-one by Brown's $\rho$-involution; but
$S_2 = c/2$ is a motivic \emph{Tate twist} $\mathbb Q(1)$-period,
not a depth-$1$ MZV. Theorem applies from weight~$3$ onwards:
$\zetasv(3) \ne 0$, $\zetasv(5) \ne 0$, $\zetasv(7) \ne 0$, \ldots
match the odd-weight shadow entries of Virasoro.

\emph{Obstruction 2 (Heegner-Chern torsion).} The Humbert divisors
$H_D\subset\overline{\mathcal A_2}$ carry Heegner-Chern classes
in $H^2_{\mot}(\overline{\mathcal A_2};\mathbb Q(1))$ with
$\mathbb Z$-graded torsion; Brown 2013 single-valued MZVs are
unconditional only over $\mathbb Q$. \emph{Resolution 2.} The
single-valued restriction is the \emph{image} of $\proj$; the
Heegner-Chern torsion lies in the \emph{kernel}
$\ker\proj\subset\MZVmot$. The two scope restrictions are
orthogonal: Humbert obstruction controls the motivic domain
(Definition~\ref{def:heeg-chern-obstruction}), single-valued
projection controls the motivic codomain. Theorem holds on
$U\cap{\proj}^{-1}(\MZVsv)$, which is the Koszul locus in
$\overline{\mathcal A_2}$ pulled back along $\proj$.

\emph{Obstruction 3 (depth-two single-valued drop).} Brown 2013
Prop.~2.5 shows $\zetasv(2) = 0$; so the Zamolodchikov norm
$c(5c+22)/10$, which has a formal depth-$2$ expansion, appears
\emph{not} to have a motivic shadow. \emph{Resolution 3.}
$c(5c+22)/10$ is a polynomial in $c$, not a period of an iterated
integral. It lies in the scalar lane (a scalar-lane
conflation hazard); its ``motivic shadow'' is
$\mathbb Q(0) = \mathrm{Ext}^0_{\MT}(\mathbb Q(0),\mathbb Q(0))$,
trivially single-valued. The single-valued scope applies to
\emph{Hochschild} periods, not to rational normalisations.

\emph{Obstruction 4 (Gangl--Kaneko--Zagier double-zeta).} Gangl--Kaneko--Zagier
2006 (\emph{Aspects of Math.}~E38) give double-zeta relations
$\zeta(a, b) = \sum \mathrm{rationals}\cdot\zeta(a+b)$ modulo
products of single zetas; these relations \emph{fail} after
single-valued projection because $\zetasv$ kills even products.
\emph{Resolution 4.} The GKZ relations are graded; the single-valued
projection respects the Hoffman grading and maps each relation to
its $\mathrm{Gal}(\CC/\RR)$-invariant part. Specifically: the
depth-$2$ weight-$n$ GKZ relations project to the single-valued
odd-weight sub-basis, recovering the $\mathrm{ker}/\mathrm{im}$
exact sequence of Brown 2013 \S 4. The scope restriction is
compatible with GKZ: the chiral-Hochschild periods lie in the
\emph{image} $\MZVsv$, obtained from GKZ by projection.

\emph{Obstruction 5 (deformation-quantization depth-three).}
Kontsevich 1999 graph weights at third order use
$\zeta(2,3)/\zeta(3,2)$ whose difference is single-valued zero
($\zetasv(2,3) - \zetasv(3,2) = \pi^2\zetasv(3)/\mathrm{rational}$
up to conventions); deformation quantization graph weights fail
the single-valued restriction. \emph{Resolution 5.} Kontsevich
deformation-quantization graphs carry full motivic periods; the
chiral-Hochschild subclass is the \emph{image} under the pushforward
along the associator $\Phi_{\mathrm{KZ}}\mapsto\Phi_{\mathrm{Del}}$
(Drinfeld associator to Deligne's even associator), which is
exactly Brown 2013 Thm.~1.1 single-valued projection. So
Kontsevich graphs live in $\MZVmot$; chiral-Hochschild pairings
live in the single-valued image $\MZVsv\subset\MZVmot$. No
contradiction; scope is preserved.

\emph{Synthesis.} Five independent obstructions refine the
scope restriction to: single-valued Hochschild pairings on the
Koszul locus of $\overline{\mathcal A_2}$, orthogonal to
Heegner-Chern torsion, compatible with GKZ double-zeta, strictly
narrower than Kontsevich deformation quantization, matching
Virasoro odd-weight shadow. The three checks of the
main motivic bar--cobar bridge
(Remark~\ref{rem:motivic-bridge-three-paths}) descend verbatim:
(i) Deligne--Goncharov 2005 motivic $\pi_1$ followed by $\proj$;
(ii) Brown 2013 single-valued MZV projection applied to the
Ikeda lift; (iii) Gangl--Kaneko--Zagier 2006 double-zeta
relations projected through $\proj$ to the single-valued
graded quotient.
\end{remark}

\begin{remark}[Cross-volume cache: motivic vs chain-level, with
single-valued scope; \ClaimStatusProvedHere]
\label{rem:cache-motivic-sv-crosslevel}
The compatibility data $\Data(\cA)$ thus inhabits \emph{three}
distinct sites, never to be conflated.
\textup{(a)} Chain-level
$\Data(\cA)\simeq B\mathrm{Aut}^h_{L_\infty}(\mathfrak g^{\infty,1}_{\cA})$
over $\mathbb C$, a $\widehat{\mathrm{grt}}_1$-torsor of
simplicial sets (Theorem~B).
\textup{(b)} Motivic $\Data^{\mot}(\cA)\in\mathcal{DM}(U;\mathbb Q)$,
a $\grt^{\mot}$-torsor in Voevodsky motives over the Humbert-free
open $U\subset\overline{\mathcal A_2,\mathbb Q}$
(Definition~\ref{def:motivic-data-groupoid}).
\textup{(c)} Single-valued $\Data^{\mathrm{sv}}(\cA)$, the image of
$\Data^{\mot}(\cA)$ under the Brown~2013 projection
$\proj_*\colon\grt^{\mot}\to\grt^{\mathrm{sv}}$, carrying
$\mathrm{Gal}(\CC/\RR)$-invariant real motivic periods
(Theorem~\ref{thm:sv-scope-restriction-chiralhoch}).
The chiral-Hochschild pairing of Theorem~H lives in (c), not in (b)
and certainly not in (a); period realisation factors as
$(b)\xrightarrow{\proj_*}(c)\xrightarrow{\mathrm{real}}(a)_\RR$.
Vol~III's two-stage factorisation
$\Phi_d = \SpCh_{\Sigma_{d-1}, C} \circ \PhiFA_d$
(Stage~1 canonical $E_d$-holomorphic factorisation algebra
$\PhiFA_d$, Stage~2 specialisation $\SpCh_{\Sigma_{d-1}, C}$ to the
reference curve $C$ via factorisation homology over a $(d{-}1)$-cycle)
inherits the same factorisation: the BKM denominator $\chi_{10}$
periods land in
$\MZVsv$, not in $\MZVmot$, because BKM denominators are
$\mathrm{Gal}(\CC/\RR)$-invariant by Borcherds 1992 Thm.~10.1
real-analytic construction. Conflation produces the error of
treating $\zetasv(3) \ne 0$ and $\zetasv(2) = 0$ identically on
both sides; at weight~$2$ the chiral-Hochschild period is forced
to be \emph{zero}, recovering class~H's concentration bound
$\mathrm{ChirHoch}^\bullet\subset\{0,1,2\}$ as a single-valued
consequence rather than an imposed condition.
\end{remark}
