% Theorem A: bar-cobar reconstruction, ordered descent, and Verdier duality.

\providecommand{\Bbarch}{\bar{B}^{\mathrm{ch}}}
\providecommand{\Omegach}{\Omega^{\mathrm{ch}}}
\providecommand{\Kosz}{\mathsf{Kosz}}
\providecommand{\Conil}{\mathsf{Conil}}
\providecommand{\SpCh}{\mathrm{Sp}^{\mathrm{ch}}}
\providecommand{\PhiFA}{\Phi^{\mathrm{FA}}}
\providecommand{\FactOp}{\mathsf{FactOp}}
\providecommand{\FactProp}{\mathsf{FactProp}}
\providecommand{\CoFact}{\mathsf{CoFact}}
\providecommand{\CoFactProp}{\mathsf{CoFactProp}}
\providecommand{\Dmod}{D\text{-}\mathsf{mod}}
\providecommand{\Tc}{\mathrm{T}^{\mathrm c}}
\providecommand{\rel}{\mathrm{rel}}
\providecommand{\PTVV}{\mathrm{PTVV}}
\providecommand{\CY}{\mathrm{CY}}
\providecommand{\Arnold}{\mathrm{Arnold}}

\chapter[Theorem $A$: Bar--Cobar Reconstruction and Verdier Duality]%
{Theorem $A$: Bar--Cobar Reconstruction and Verdier Duality}
\label{ch:theorem-A-infinity-2}\label{chap:theorem-A-infinity-2}

\section*{Notation, hypotheses, and lane structure}

Theorem~A has three pieces. The chiral cobar and chiral bar functors
form the adjunction
\[
\Omegach_X\;:\;\CoAlg^{\fact,\conil,\co}_X
\;\rightleftarrows\;\Alg^{\fact,\aug,\comp}_X
\;:\;\Bbarch_X,
\qquad \Omegach_X\dashv \Bbarch_X,
\]
and the algebra-side counit reconstructs a Koszul algebra:
\[
\varepsilon_\cA\colon \Omegach_X\Bbarch_X(\cA)\xrightarrow{\sim}\cA
\qquad (\cA\in\Kosz(X)).
\]
The Verdier-dualized Koszul duality functor is the different operation
\[
K_X(\cA):=\Omegach_X\mathbb D_{\Ran}\Bbarch_X(\cA).
\]
Bar--cobar reconstruction is inversion on the Koszul locus;
Koszul duality enters only after Verdier duality on the Ran bar
coalgebra.
The notation is fixed throughout this chapter:
$\cA$ is the algebra, $\Bbarch_X(\cA)$ is the bar coalgebra,
$\cA^i:=H^\bullet\Bbarch_X(\cA)$ is the Koszul-dual coalgebra when
this cohomology is finite enough to exist in the ordinary category,
$\cA^!$ is the algebra obtained from the appropriate linear or Verdier
dual of $\cA^i$, and
$Z^{\mathrm{der}}_{\ch}(\cA)=C^\bullet_{\ch}(\cA,\cA)$ is the derived
centre. None of these objects is $R_X(\cA)$.

The same structure has eight standard faces: twisting-morphism adjunction,
counit quasi-isomorphism, unit
weak equivalence, twisted tensor acyclicity, bar concentration in
weight~$1$, SC-formality, $R$-twisted $\Sigma_n$-descent, and the
Francis--Gaitsgory $(\infty,2)$-equivalence on the properadic envelope
of the chiral associative bar--cobar pair.

\paragraph{Three uniform hypotheses (H1--H3).}
Let $X$ be a smooth projective curve over a field $k$ of
characteristic~$0$. The Koszul reflection of Theorem~A holds for
factorization $\Eone$-algebras $\cA$ on $X$ satisfying:
\begin{itemize}
\item[\textup{(H1)}] \emph{Augmentation.}
$\cA\in\Alg^{\fact,\aug}_X$. Required to define the augmentation
ideal~$\bar\cA=\ker(\varepsilon)$.
\item[\textup{(H2)}] \emph{Augmentation-ideal completeness.}
$\cA\simeq\varprojlim_n \cA/\bar\cA^{\,n}$. Required for the bar--cobar
twisted tensor product to converge unconditionally; equivalently,
$\cA$ is \emph{weakly curved} in Positselski's sense
(\cite[Mem.\ AMS]{Positselski2018}).
\item[\textup{(H3)}] \emph{Finite-dimensional graded bar pieces.}
Each conformal-weight space
$\bigl(\Bbarch_X(\cA)\bigr)_{w}$ $(w\in\mathbb Z_{\geq 0})$ is
finite-dimensional when the bar complex is graded by the total
conformal weight of the tensor factors, not by the bar-tensor depth.
Required for ordinary acyclicity to follow from coacyclicity
(\cite[Appendix~A.5, covariantly weighted]{Positselski2011});
witnessed archetype-by-archetype in
Lemma~\ref{lem:archetype-H123-witness}.
\end{itemize}
Hypotheses (H1)--(H3) are the published bar--cobar Quillen
equivalence hypotheses (Vallette~\cite{Val16},
Positselski~\cite{Positselski2018,Positselski2011}, Hinich~\cite{Hinich2003})
specialised to the chiral ambient. They subsume the separate
per-clause hypotheses (conilpotency, completeness, Koszulness,
finite-dim graded pieces) into a single uniform set.

\paragraph{Parametric strength taxonomy.}
\label{par:A-strength-taxonomy}%
\index{Theorem A!parametric strength}%
Theorem~A is read at three calibrated strengths, separated by which
hypothesis package is invoked and which lane carries the proof.
\begin{itemize}
\item[\textsc{Weak (always-on adjunction).}]
\emph{Type signature:} (Open quadrant; bar--cobar; Beilinson level
$1\!\leftrightarrow\!2$; HP = augmented + complete = (H1)+(H2)).
There is an adjunction
$\Omegach_X\dashv\Bbarch_X$ on
$\CoAlg^{\fact,\conil,\co}_X\rightleftarrows\Alg^{\fact,\aug,\comp}_X$
with the universal twisting morphism $\tau\colon\Bbarch_X(\cA)\to\cA$
as Maurer--Cartan element. No reconstruction $K^2\simeq\id$ is asserted.
This is the Vallette--Hinich Quillen pair on the chiral ambient
(Theorem~\ref{thm:koszul-reflection}\ref{KR-i}; LV12 Theorem~2.2.9).
\item[\textsc{Strong (reconstruction on $\Kosz(X)$).}]
\emph{Type signature:} (Open quadrant; bar--cobar reconstruction;
Beilinson level $1\!\leftrightarrow\!2$; HP = augmented + complete +
finite-dim graded + Koszul locus = (H1)+(H2)+(H3) restricted to
$\Kosz(X)$). The counit
$\varepsilon_\cA\colon\Omegach_X\Bbarch_X(\cA)\xrightarrow{\sim}\cA$
is a chain-level quasi-isomorphism on the Koszul locus. This is
$K^2\simeq\id$ on $\Kosz(X)$, i.e.\ \emph{inversion} of bar by cobar
on the locus where the bar weight collapses at $E_2$
(Theorem~\ref{thm:koszul-reflection}\ref{KR-ii};
Theorem~\ref{thm:ftm-seven-fold-tfae-via-hub-spoke} hub).
\item[\textsc{Strongest (rejected): $K^2\simeq\id$ everywhere.}]
\emph{Status:} \textbf{REJECTED.} Off the Koszul locus the bar--cobar
counit fails to be a chain-level quasi-isomorphism: the bar complex
acquires higher Stasheff--Massey shadows $S_k$ ($k\geq 3$) recording
non-formality. The would-be universal reconstruction
$K^2\simeq\id$ on all of $\Alg^{\fact,\aug,\comp}_X$ is therefore
\emph{false} as stated; the surviving statement is the chiral
Hochschild concentration theorem (\textbf{Theorem~H},
$\ChirHoch^\bullet\subset\{0,1,2\}$ on the locus where (H1)--(H3)
hold, with class~$\mathsf{M}$ requiring the pro-conilpotent
weight-completed ambient of
Remark~\ref{rem:class-M-pro-conilpotent}). The shadow tower $S_k$
populates $\ChirHoch^2$; bar concentration in weight~$1$ at $g\geq 1$
is class-$\mathsf G$ only, with fiberwise curvature
$d^2_{\mathrm{fib}}=\kappa\cdot\omega_g$ obstructing the universal
form. The off-Koszul theorem is the weight-completed coderived
continuation of clause~\ref{KR-iii}, not strict
$K^2\simeq\id$.
\end{itemize}
The forbidden form ``$K^2\simeq\id$ everywhere'' confuses the shadow
with the object along the forgetful functor
$\Alg^{\fact,\aug,\comp}_X\twoheadrightarrow\Kosz(X)$: the Koszul
locus is the sublocus on which the reconstruction theorem holds, and
extending it without weight completion treats the locus as the
ambient. The weight-completed Positselski continuation in
clause~\ref{KR-iii} is the correct off-locus replacement; Theorem~H is
the Hochschild concentration that survives.

\paragraph{Lane split: Priddy versus Positselski.}
\label{par:A-priddy-vs-positselski}%
\index{Theorem A!Priddy lane vs Positselski lane}%
\index{Priddy lane!chain-level Theorem A}%
\index{Positselski lane!coderived Theorem A}%
The same theorem has two lanes whose proofs and ambients are
disjoint, and which must not be conflated.
\begin{itemize}
\item[\textsc{Priddy lane (chain-level).}]
\emph{Ambient:} weight-graded chain complexes
$\mathrm{Ch}(\mathrm{Vect}^{\mathbb Z_{\geq 0}\text{-gr}}_{\mathrm{fin}})$
of positive-energy graded objects with finite-dimensional
weight pieces (Remark~\ref{rem:H3-not-finite-bar-depth}).
\emph{Statement:} chain-level quasi-isomorphism
$\Omegach_X\Bbarch_X(\cA)\xrightarrow{\sim}\cA$ on $\Kosz(X)$,
witnessed by a Priddy--Koszul chain homotopy $h$ contracting the
augmentation ideal of the bar resolution
(\cite{Priddy70};
\cite[Theorem~7.4.1]{LV12}; chiral specialisation transferred via
Theorem~\ref{thm:hackney-robertson-model}).
\emph{Witness object:} the weight-graded archetype dimension
generating function $P(q)/(1-P(q))$ of
Lemma~\ref{lem:archetype-H123-witness}, which witnesses (H3) and
forces $E_2$-collapse of the bar--cobar spectral sequence
weight-by-weight.
\item[\textsc{Positselski lane (coderived/contraderived).}]
\emph{Ambient:} the
$D^{\mathrm{co}}\!\!-\!\!D^{\mathrm{ctr}}$
weight-completed Positselski surface
\cite{Positselski2018,Positselski2011}, on the pro-conilpotent
completion $\widehat{\cA}=\varprojlim_N\cA/\cA_{\geq N}$.
\emph{Statement:} the coderived/contraderived bar--cobar duality
\[
D^{\mathrm{co}}\bigl(\Bbarch_X(\cA)\text{-}\Comod^{\fact,\conil}\bigr)
\;\simeq\;
D^{\mathrm{ctr}}\bigl(\Omegach_X\Bbarch_X(\cA)\text{-}\Mod^{\fact,\comp}\bigr),
\]
extending the Priddy chain-level statement off $\Kosz(X)$ at the
cost of replacing chain-level acyclicity by coacyclicity. This is
the lane on which class-$\mathsf{M}$ archetypes (Virasoro,
$\cW_N$) and the curved $A_\infty$-genus
filtration~$\psi_g$ live. \emph{Witness object:} the weakly curved
$A_\infty$-algebra $(\widehat{\cA}, m_0=\kappa\cdot\omega_g, m_1,
m_2,\dots)$ over the complete local base parameterised by the level
or central charge \cite[Theorem~9.1]{Positselski2018}.
\end{itemize}
The two lanes coincide on $\Kosz(X)$ (Priddy embeds into Positselski
as the formal locus where the higher Stasheff operations vanish);
they diverge off $\Kosz(X)$, where Priddy fails and Positselski
survives in the coderived ambient. Theorem~A as stated is the
\emph{Priddy} lane on $\Kosz(X)$ together with the \emph{Positselski}
lane off $\Kosz(X)$, glued by the (H3) finite-graded condition that
realises the ordinary--coderived comparison
\cite[Appendix~A.5]{Positselski2011}. Identifying the ordinary
ambient with the completed ambient is the precise prohibition against
naming Theorem~A in the Priddy lane on a class-$\mathsf{M}$ algebra
without the pro-conilpotent completion.

\paragraph{Four lanes by categorical level.}
\label{par:A-four-lanes}%
\index{Theorem A!four lanes by categorical level}%
The same statement of Theorem~A appears in four ambients of
increasing categorical strength, each with a published Quillen or
adjoint-equivalence theorem as the load-bearing input:
\begin{enumerate}[label=\textsc{L\arabic*.}]
\item \label{L1-chain} \emph{Chain level
($1$-categorical).} Bar--cobar adjunction in
$\mathrm{Ch}(\mathrm{Vect})$ with explicit Priddy contraction on
$\Kosz(X)$; Theorem~\ref{thm:bar-cobar-isomorphism-main} (chiral
ambient transfer of \cite[Theorem~11.4.1]{LV12}). Witness: explicit
chain homotopy $h_{A_b}$ of the form below.
\item \label{L2-quillen} \emph{Quillen-equivalence level
($1$-categorical with model structure).}
Bar--cobar Quillen equivalence on conilpotent dg coalgebras versus
augmented complete dg algebras, in the ambient
$(\Fact(X),\star)$ (Francis--Gaitsgory--Rozenblyum,
\cite[Chapter~IV.5, Theorem~3.1.2]{GR17}); the Vallette
\cite[Theorem~2.1]{Val16} chain-level statement specialises to this
ambient through the GR17 transfer (Remark~\ref{rem:ainf2-heal-72}).
\item \label{L3-infty1} \emph{$(\infty,1)$-categorical level.}
Bar--cobar adjoint equivalence between
$\Fact^{\aug}(X)$ and $\CoFact^{\conil,\comp}(X)$ in the
$(\infty,1)$-localisation of the Quillen pair of \ref{L2-quillen};
Lurie HA \S5.5 supplies the parallel topological case.
\item \label{L4-infty2} \emph{$(\infty,2)$-properad level.}
Theorem~$A^{\infty,2}$ (Theorem~\ref{thm:A-infinity-2}):
$(\infty,2)$-categorical adjoint equivalence between
$\FactProp^{\aug}_{\langle\chirAss\rangle}(X)$ and
$\CoFactProp^{\conil,\comp}_{\langle\chirAss\rangle}(X)$ on the
conilpotent-complete properadic envelope generated by the chiral
associative bar--cobar pair, lifted along
$\FactOp(X)\hookrightarrow\FactProp(X)$ via Hackney--Robertson
\cite[Theorem~5.12]{HackneyRobertson2019}.
\end{enumerate}
The downstream specialisations of
Corollary~\ref{cor:ainf2-downstream-list} use \ref{L1-chain} and
\ref{L4-infty2} explicitly; \ref{L2-quillen} and \ref{L3-infty1} are
intermediate transfers fixed by Hinich \cite{Hinich2003} and the
GR17 model-categorical localisation.

The only locus on which any hypothesis is restrictive is~(H3): the
non-finitely-generated MC4-completion regime fails (H3) and is
therefore the sole genuinely open frontier
(Conjecture~$\Pi 4$ of \S\ref{sec:ainf2-platonic-obstructions}). The
standard landscape -- Heisenberg ($\mathsf{G}$), affine Kac--Moody at
noncritical level ($\mathsf{L}$), $\beta\gamma_\lambda$ ($\mathsf{C}$),
Virasoro and principal $\mathcal{W}_N$ ($\mathsf{M}$), Mukai-doubled
lattice ($\mathsf{B}$) -- satisfies all three hypotheses uniformly on
the conformal-weight grading, with the class-$\mathsf{M}$ case
requiring the pro-conilpotent weight completion
$\widehat{\cA}=\varprojlim_N\cA/\cA_{\geq N}$ in place of the raw
direct-sum ambient (Remark~\ref{rem:class-M-pro-conilpotent}).

\paragraph{Notion of $\Eone$-chiral algebra in use.}
Five distinct notions of $\Eone$-chiral algebra coexist and must never
be interchanged: (A) strict $\chirAss$-algebra; (B) $A_\infty$-algebra
in the chiral endomorphism operad $\End^{\ch}_\cA$; (C)
Etingof--Kazhdan quantum vertex algebra; (D) $A_\infty$-algebra in
$\Eone$-chiral; (E) factorization on $\Ran^{\ord}(X)$. Each notion
carries its own derived centre. The Drinfeld associator compares
(B) and (C) only after a quantized braided descent datum has been
chosen on the Koszul locus; Theorem~A itself is not a
quantization theorem. Theorem~A is stated in
\emph{Notion~B}: $A_\infty$-algebras in the chiral endomorphism
operad $\End^{\ch}_\cA$ on the curve~$X$, with spectral parameters
realised as formal algebraic variables on $\Ran^{\ord}(X)$. The
pole-free restriction~\ref{A2-ii} recovers \emph{Notion~A}
(strict $\chirAss$-algebras) at a marked point. The
ordered-to-symmetric descent~\ref{A2-iii} relates Notion~B
(ordered) to Notion~D (double $A_\infty$-promoted) only when a
unitary quantum $R$-descent datum satisfying
Lemma~\ref{lem:R-twisted-descent} is part of the input. The chiral
coassociative coalgebra structure on $\Bbarch_X(\cA)$
is over $(\chirAss)^!$, never over $\SCchtop$: the
Swiss--cheese structure $\SCchtop$ emerges on the derived centre pair
$(C^{\bullet}_{\ch}(\cA,\cA),\cA)$, not on $\Bbarch_X(\cA)$ itself.

\begin{convention}[Ordered bar signs and desuspension]
\label{conv:A-infinity-2-ordered-bar-signs}
\index{ordered bar complex!desuspension signs}
\index{bar differential!ordered sign convention}
The cohomological convention is $|d|=+1$ and
$|s^{-1}a|=|a|-1$. For homogeneous $a_i\in\bar\cA$ the ordered bar
coalgebra is
\[
B_X^{\ord}(\cA)=T^c(s^{-1}\bar\cA)
\]
with deconcatenation coproduct. Its differential is the coderivation
whose unary and binary projections are
\[
b_1(s^{-1}a)=-s^{-1}(d_\cA a),\qquad
b_2^{(r)}(s^{-1}a\otimes s^{-1}b)
=(-1)^{|a|}s^{-1}(a_{(r)}b),
\]
and whose action on the $i$-th adjacent pair carries the prefix sign
\[
(-1)^{\sum_{q<i}(|a_q|-1)+|a_i|}.
\]
For an $A_\infty$-chiral algebra, the higher maps are extended by the
same desuspended coderivation rule. With this convention
$d_{B^{\ord}}^2=0$ is precisely the desuspended Stasheff identity
together with the Arnold relation on logarithmic collision forms.
The symmetric bar is obtained from this ordered complex by the
$R$-twisted descent of Lemma~\ref{lem:R-twisted-descent}; no additional
sign convention is introduced in the symmetric lane.
\end{convention}

%================================================================
\section{Bar-cobar reconstruction and Verdier duality: unified Theorem~A}\label{sec:ainf2-koszul-reflection}
%================================================================

\subsection{Bar--cobar adjunction, reconstruction on the Koszul locus, and Verdier duality}

\begin{theorem}[Theorem~A: bar-cobar adjunction, reconstruction, and Verdier duality;
\ClaimStatusConditional]
\label{thm:koszul-reflection}
\index{Theorem A!bar-cobar reconstruction and Verdier duality}
\index{Koszul duality!Verdier-dualized chiral form}
\index{bar-cobar!reconstruction}
Let $X$ be a smooth projective curve over a field~$k$ of
characteristic~$0$. Under hypotheses \textup{(H1)}--\textup{(H3)} of
\S\textup{Setup}, the canonical chiral bar-cobar adjunction is
\[
\Omegach_X\;:\;\CoAlg^{\fact,\conil,\co}_X
\;\rightleftarrows\;
\Alg^{\fact,\aug,\comp}_X
\;:\;\Bbarch_X,
\qquad \Omegach_X\dashv\Bbarch_X .
\]
The reconstruction and Koszul-duality functors are different:
\[
R_X(\cA):=\Omegach_X\Bbarch_X(\cA),
\qquad
K_X(\cA):=\Omegach_X\,\mathbb{D}_{\Ran}\Bbarch_X(\cA).
\]
The first is bar-cobar reconstruction. The second is the
Verdier-dualized chiral Koszul duality functor. The following
statements hold in the stable presentable factorization ambient:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \label{KR-i} \emph{Adjunction.}
$\Omegach_X\dashv\Bbarch_X$ with unit
$\eta_\cC\colon\cC\to\Bbarch_X\Omegach_X(\cC)$ on coalgebras and
counit
$\varepsilon_\cA\colon\Omegach_X\Bbarch_X(\cA)\to\cA$ on algebras.
\item \label{KR-ii} \emph{Reconstruction on $\Kosz(X)$.}
On the Koszul locus
$\Kosz(X)\subset\Alg^{\fact,\aug,\comp}_X$, the equivalence restricts
to one valued in \emph{ordinary} (non-coderived) factorization
coalgebras. The counit is a chain-level quasi-isomorphism
\[
\varepsilon_\cA\colon R_X(\cA)=\Omegach_X\Bbarch_X(\cA)
\xrightarrow{\sim}\cA .
\]
\item \label{KR-iii} \emph{Weight-completed coderived continuation off
$\Kosz(X)$.}
For $\cA\in\Alg^{\fact,\aug,\comp}_X\setminus\Kosz(X)$, the identity
$R_X(\cA)\simeq\cA$ is asserted only on the
weight-completed / pro-conilpotent Positselski surface. The raw
direct-sum class-$\mathsf M$ bar coalgebra is not covered by this
clause.
\item \label{KR-iv} \emph{Verdier duality.}
The chiral Koszul dual is obtained by applying Verdier duality to
the bar object before cobar:
$K_X(\cA)=\Omegach_X\mathbb{D}_{\Ran}\Bbarch_X(\cA)$.
This is the lane that identifies
$\mathbb{D}_{\Ran}\Bbarch_X(\cA)$ with the factorization
Koszul-dual coalgebra $\cA^{!,\mathrm{co}}_{\infty}$. The algebraic
Koszul dual is obtained only after cobar:
$\cA^!_\infty=\Omegach_X(\cA^{!,\mathrm{co}}_{\infty})$.
\item \label{KR-v} \emph{Chain-level and categorical forms.}
The chain-level representative of the theorem is the bar--cobar
bicomplex with the desuspended differential of
Convention~\ref{conv:A-infinity-2-ordered-bar-signs} and the counit
$\varepsilon_\cA$. The $(\infty,1)$- and $(\infty,2)$-categorical
statements are obtained by localising this chain-level construction
at quasi-isomorphisms and then imposing the factorization/properadic
universal properties. The categorical statement does not replace the
chain-level quasi-isomorphism, and the chain model does not assert a
strict equality before localisation.
\end{enumerate}
\end{theorem}

\begin{proof}
The abstract bar--cobar adjunction is
Proposition~\ref{prop:universal-twisting-adjunction} (LV12
Theorem~2.2.9): there is
a natural bijection
$\Hom_{\dgCoAlg}(\cC,B(A))\simeq\Tw(\cC,A)\simeq\Hom_{\dgAlg}(\Omega(\cC),A)$
mediated by the convolution algebra. The chiral specialisation uses
the chiral operad, which is Koszul by Beilinson--Drinfeld~\cite[\S3.6]{BD04}.
Vallette's bar--cobar Quillen equivalence
(\cite[Theorem~2.1]{Val16}) applies to the Koszul-resolved chiral
operad in the symmetric-monoidal ambient $\Fact(X)$ under~$\star$
(\cite[\S4.2]{Francis2012}; promoted to $(\infty,2)$ in
\cite[Chapter~IV.5]{GR17}, see
Proposition~\ref{prop:fg-ambient-properties}); promotion to a
symmetric-monoidal Quillen equivalence uses
Hinich~\cite[\S6]{Hinich2003}.

Curvature (the nonzero $m_0$ at higher genus) is absorbed by
Positselski~\cite[Theorem~9.1]{Positselski2018}: weakly curved
$A_\infty$-algebras over a complete local ring fit into an explicit
Quillen equivalence with conilpotent CDG-coalgebras under (H1)+(H2).
The factorization-compatible refinement is the stratumwise Positselski
equivalence together with the Verdier-quotient assembly in the
Francis--Gaitsgory factorization ambient. Promotion from the coderived
equivalence~\ref{KR-iii} to the
chain-level qi of~\ref{KR-ii} on $\Kosz(X)$ follows from the
$E_2$-collapse of the bar--cobar spectral sequence
(Theorem~\ref{thm:ftm-seven-fold-tfae-via-hub-spoke}) plus
\cite[Appendix~A.5, covariantly weighted]{Positselski2011} which under
hypothesis~(H3) identifies coacyclicity with chain-level acyclicity.

The reconstruction statement \ref{KR-ii} is the counit equivalence
$R_X(\cA)=\Omegach_X\Bbarch_X(\cA)\xrightarrow{\sim}\cA$ on the
Koszul locus. The unit
$\cC\to\Bbarch_X\Omegach_X(\cC)$ belongs to the coalgebra side of the
same adjunction. Off~$\Kosz(X)$, \ref{KR-iii} is the corresponding
statement after weight completion and passage to the
coderived/contraderived Positselski surface. Clause~\ref{KR-iv}
records the separate Verdier-dualized Koszul-duality functor; it is
not the bar-cobar reconstruction functor.

Functoriality and Koszul-locus properties extend to the symmetric
monoidal $(\infty,2)$-level by the universal property of the adjoint
equivalence; the explicit $(\infty,2)$-form on the properadic envelope is
Theorem~\ref{thm:A-infinity-2} in \S\ref{sec:ainf2-main}.
\end{proof}

\subsection{The single diagram and the single equation}

The bar-cobar adjunction is captured by one diagram:
\[
\begin{tikzcd}[column sep=large,row sep=large]
\CoAlg^{\mathrm{fact},\mathrm{conil},\mathrm{co}}_X
 \arrow[r,bend left=15,"\Omegach_X"]
 \arrow[r,phantom,"\rotatebox{90}{$\dashv$}"description]
&
\Alg^{\mathrm{fact},\mathrm{aug},\mathrm{comp}}_X
 \arrow[l,bend left=15,"\Bbarch_X"]
\end{tikzcd}
\qquad
\Omegach_X\dashv\Bbarch_X .
\]
And by one equation:
\[
\boxed{
\Omegach_X\dashv\Bbarch_X,\qquad
\Omegach_X\Bbarch_X\simeq\mathrm{id}_{\Alg}\text{ on }\Kosz(X),\qquad
\id_{\CoAlg}\to\Bbarch_X\Omegach_X\text{ is the coalgebra unit}.
}
\]

\begin{remark}[Reconstruction and duality are separate operations]
\label{rem:reconstruction-duality-separation}
\index{bar-cobar!reconstruction versus Verdier duality}
The counit $\Omegach_X\Bbarch_X(\cA)\to\cA$ is reconstruction. The
Verdier-dualized object
$\mathbb D_{\Ran}\Bbarch_X(\cA)$ is the Koszul-dual coalgebra lane.
Conflating these two operations turns inversion into a false
involutivity statement.
\end{remark}

\begin{remark}[Four named morphisms in Theorem~A]
\label{rem:four-named-morphisms}
\index{Koszul reflection!four named morphisms}
Four canonical morphisms organize the theorem:
\begin{itemize}
\item $\eta_\cC\colon\cC\to\Bbarch_X\Omegach_X(\cC)$ -- the
coalgebra-side unit;
\item $\varepsilon_\cA\colon\Omegach_X\Bbarch_X(\cA)\to\cA$ -- the
algebra-side counit, chain-level qi on
$\Kosz(X)$;
\item $K_X(\cA)=\Omegach_X\mathbb D_{\Ran}\Bbarch_X(\cA)$ -- the
Verdier-dualized Koszul-duality functor;
\item $\psi(\hbar)$ -- the \emph{genus-completed counit}, the
$\hbar$-adic series
$\psi(\hbar)=\sum_g\hbar^{2g-2}\psi_g$ over the genus filtration on
$\Bbarch_g(\cA)$, with quantum correction
$m_0^{(g)}=\kappa(\cA)\,\omega_g$ as the $\hbar$-flatness
obstruction.
\end{itemize}
\end{remark}

\begin{proposition}[Ambient firewall for modules and completions;
\ClaimStatusConditional]
\label{prop:A-module-completion-firewall}
\index{Theorem A!module and completion ambient}
\index{coderived category!bar-cobar continuation}
Let $\cA$ satisfy \textup{(H1)}--\textup{(H3)}. The morphism
$\varepsilon_\cA\colon\Omegach_X\Bbarch_X(\cA)\to\cA$ belongs to
$\Alg^{\fact,\aug,\comp}_X$ and is a chain-level quasi-isomorphism
only on $\Kosz(X)$. For a complete left $\cA$-module $M$, the
twisted bar module
\[
\Bbarch_X(\cA)\otimes^{\tau} M
\]
is a resolution used to compute derived $\cA$-module functors after
restriction along~$\varepsilon_\cA$; it is not a statement that all
ordinary $\cA$-modules are equivalent to ordinary
$K_X(\cA)$-modules. Off the Koszul locus the surviving module theorem
is the Positselski surface
\[
D^{\mathrm{co}}\bigl(\Bbarch_X(\cA)\text{-}\mathsf{Comod}^{\fact,\conil}\bigr)
\;\simeq\;
D^{\mathrm{ctr}}\bigl(\Omegach_X\Bbarch_X(\cA)\text{-}\mathsf{Mod}^{\fact,\comp}\bigr),
\]
after the same weight completion as in \textup{(H2)}--\textup{(H3)}.
The Verdier-dualized functor
$K_X(\cA)=\Omegach_X\mathbb D_{\Ran}\Bbarch_X(\cA)$ enters only after
replacing the bar coalgebra by its Ran Verdier dual; it is not the
target of the reconstruction counit.
\end{proposition}

\begin{proof}
The first assertion is the source and target statement of
Theorem~\ref{thm:koszul-reflection}. On $\Kosz(X)$,
$\varepsilon_\cA$ is a quasi-isomorphism, hence restriction of scalars
along $\varepsilon_\cA$ identifies the derived categories of complete
modules by the usual invariance of derived module categories under a
quasi-isomorphism of complete dg algebras. The twisted complex
$\Bbarch_X(\cA)\otimes^\tau M$ is the standard bar resolution
associated to the universal twisting morphism
$\tau\colon\Bbarch_X(\cA)\to\cA$.

If $\cA\notin\Kosz(X)$, the cone of $\varepsilon_\cA$ need not be
ordinary acyclic. Positselski's bar--cobar duality for complete weakly
curved algebras and conilpotent CDG-coalgebras
\cite[Theorem~9.1]{Positselski2018}, together with the covariantly
weighted criterion of \cite[Appendix~A.5]{Positselski2011}, gives the
displayed coderived/contraderived comparison after the (H2) completion
and the (H3) finite-weight hypothesis. Verdier duality changes the
coalgebra input before cobar; it is therefore a separate functorial
operation.
\end{proof}

\begin{remark}[Bar coalgebra structure is over $(\chirAss)^{!}$,
not over $\SCchtop$]
\label{rem:bar-over-chirAss-shriek}

\index{SC-chtop!emerges on derived centre, not on bar}
The output coalgebra $\Bbarch_X(\cA)\in\CoAlg^{\fact,\conil,\co}_X$ is
a single chiral coassociative coalgebra over the chiral cooperad
$(\chirAss)^{!}$, with deconcatenation coproduct and the bar
differential as a single degree-$1$ map. The Swiss--cheese
$\SCchtop$ structure does \emph{not} live on $\Bbarch_X(\cA)$. The
$\SCchtop$ structure, or the $E_3$-topological structure with
conformal vector, emerges on the derived centre pair
$(C^{\bullet}_{\ch}(\cA,\cA),\cA)$, computed \emph{using}
$\Bbarch_X(\cA)$ as a resolution. The bar coalgebra is the
$\Eone$-input of the Koszul reflection; the derived centre is the
$\SCchtop$/$E_3$-topological output.
\end{remark}

\subsection{Archetype witnesses of (H1)--(H3)}
\label{subsec:archetype-witness-H123}

The claim that the five archetypes
$\mathsf{G}$ (Heisenberg/free field), $\mathsf{L}$ (affine Kac--Moody at
noncritical level), $\mathsf{C}$ (contact $\beta\gamma_\lambda$),
$\mathsf{M}$ (Virasoro, principal $\mathcal{W}_N$), $\mathsf{B}$
(Mukai-doubled lattice, Borcherds/BKM) sit inside the
(H1)+(H2)+(H3) locus requires per-archetype witnesses, because
(H3) -- finite-dimensionality of each conformal-weight space of
$\Bbarch_X(\cA)$ -- is formulated on the \emph{bar} side, not on $\cA$
itself, and the standard landscape carries vertex-operator
algebras of unbounded conformal weight. The witness table records
the exact grading on which (H3) holds and the exact completion on
which (H2) holds.

\begin{lemma}[Archetype witnesses for (H1)--(H3); \ClaimStatusProvedHere]
\label{lem:archetype-H123-witness}
\index{hypothesis H3!archetype witness table}%
\index{archetype!(H1)--(H3) witness}%
\index{Virasoro!(H3) witness by conformal weight}%
\index{Mukai doubling!(H3) witness on Koszul locus}%
For each archetype the augmented factorization algebra
$(\cA,\varepsilon)$ satisfies hypotheses \textup{(H1)--(H3)} of
\S\textup{Setup}, witnessed by the conformal-weight grading
$\cA=\bigoplus_{n\geq 0}\cA_n$ and the bar-$n$-filtration
$F^{\mathrm{bar}}_{\bullet}\Bbarch_X(\cA)$. The witnesses are:
\begin{center}
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{@{}llll@{}}
\toprule
Archetype & $\bar\cA_n$ generators & $\dim_k\bar\cA_n=d_n$ & Completion for (H2)\\
\midrule
$\mathsf{G}$ (Heis.)
 & $\alpha_{-n}$, $n\geq 1$
 & $p(n)-[n=0]$
 & $\hbar$-adic\\
$\mathsf{L}$ ($\widehat{\fg}_k$)
 & $J^a_{-n}$, $n\geq 1$, $a\leq\dim\fg$
 & $p(n)\dim\fg$ (leading)
 & level-filtered\\
$\mathsf{C}$ ($\beta\gamma_\lambda$)
 & $\beta_{-n-\lambda}$, $\gamma_{-n+\lambda-1}$
 & $2\,p(n)$ (leading)
 & conformal-weight\\
$\mathsf{M}$ ($\mathrm{Vir}_c$)
 & $L_{-n}$, $n\geq 2$
 & $p_{\geq 2}(n)$
 & conformal-weight\\
$\mathsf{M}$ ($\mathcal{W}_N$)
 & $W^{(k)}_{-n}$, $2\leq k\leq N$, $n\geq k$
 & $p_{\geq 2,3,\ldots,N}(n)$
 & conformal-weight\\
$\mathsf{B}$ (Mukai-doubled)
 & $II_{4,20}$ basis $\otimes t^{-n}$, $n\geq 1$
 & $24\,p(n)$
 & lattice-level\\
\bottomrule
\end{tabular}
\end{center}
Here $p(n)$ is the partition function, $p_{\geq k}(n)$ the number of
partitions of $n$ into parts $\geq k$, $p_{\geq 2,\ldots,N}(n)$ the
number of partitions of $n$ into parts labelled by an integer
$k\in\{2,\ldots,N\}$ with part of label $k$ having size $\geq k$, and
$24=\rk II_{4,20}$ is the rank of the Mukai lattice of K3.
The bar weight-$w$ dimension is in each case
\[
\dim_k \bigl(\bar B^{\mathrm{ch}}(\cA)\bigr)_w
 \;=\;
 \sum_{p\geq 1}\;
 \sum_{w_1+\cdots+w_p=w,\,w_i\geq w_{\min}}\;
 d_{w_1}\cdots d_{w_p}
 \;=\; [q^w]\,\frac{P(q)}{1-P(q)},
\]
with $P(q)=\sum_{n\geq w_{\min}}d_n q^n$ the Poincar\'e series of
$\bar\cA$ and $w_{\min}\in\{1,2\}$ the minimum conformal weight of a
generator. Because $P(q)$ has zero constant term, the formal quotient
$P(q)/(1-P(q))$ has well-defined finite coefficients, so each weight-$w$
dimension is finite and (H3) holds on the conformal-weight grading
uniformly across all five archetypes.
\end{lemma}

\begin{proof}
\emph{(H1)} is the augmentation $\varepsilon\colon\cA\to\omega_X$
projecting onto the vacuum/bosonic-zero-mode sector; all five
archetypes are standard augmented vertex-operator algebras
\cite[\S3.4]{FBZ04}.

\emph{(H2)} is the completeness of $\cA$ with respect to the
augmentation ideal $\bar\cA=\ker(\varepsilon)$. In each archetype the
conformal-weight filtration $F_N\cA=\cA_{\leq N}$ is compatible with
the augmentation ideal: $(\bar\cA)^m\subset\cA_{\geq m}$ by the
positive-energy property of the OPE, so the $\bar\cA$-adic completion
is dominated by the conformal-weight completion. For Heisenberg and
free-field archetypes the two completions coincide; for
$\mathsf{L}$ the level filtration $\hbar\leftrightarrow k^{-1}$ is
compatible with the conformal grading via the Sugawara construction;
for $\mathsf{M}$ the conformal completion is itself the $\bar\cA$-adic
completion by Feigin--Fuchs (\cite{FF84}); for $\mathsf{B}$ the
Mukai-doubled lattice is Kac--Moody on a hyperbolic extension and the
level filtration is again compatible.

\emph{(H3)} is finite-dimensionality of $\Bbarch_X(\cA)_w$ for each
conformal weight $w$. The bar complex
$\bar B^{\mathrm{ch}}_p(\cA)=\bar\cA^{\otimes p}$ inherits the total
conformal-weight grading; at bar-depth $p$ and total conformal weight
$w$ the dimension is
\[
\dim_k\bigl(\bar B^{\mathrm{ch}}_p(\cA)\bigr)_w
 \;=\;
 \sum_{w_1+\cdots+w_p=w,\,w_i\geq w_{\min}}
 \prod_{i=1}^{p} d_{w_i}
 \;<\;\infty,
\]
because the set of compositions of $w$ into $p$ parts each
$\geq w_{\min}$ is finite, and each factor $d_{w_i}=\dim_k\bar\cA_{w_i}$
is finite by positive-energy PBW. Summing over $p\leq w/w_{\min}$
produces the tabulated generating-function dimension via the geometric
identity $\sum_{p\geq 1}P(q)^p=P(q)/(1-P(q))$.
Explicit first values for Virasoro
($d_n=p_{\geq 2}(n)$: $d_2=1$, $d_3=1$, $d_4=2$, $d_5=2$, $d_6=4$,
$d_7=4$) give
$\dim \bar B^{\mathrm{ch}}(\mathrm{Vir}_c)_w$ as the coefficient of
$q^w$ in
$P(q)/(1-P(q))$ with
$P(q)=q^2+q^3+2q^4+2q^5+4q^6+4q^7+\cdots$; the numerics
$w=2\colon 1$, $w=3\colon 1$, $w=4\colon 3$, $w=5\colon 4$,
$w=6\colon 10$, $w=7\colon 15$, enumerable as a direct check.
\end{proof}

\begin{remark}[What (H3) is \emph{not}]
\label{rem:H3-not-finite-bar-depth}
\index{hypothesis H3!vs bar-depth finiteness}%
Hypothesis (H3) is finite-dimensionality of each conformal-weight
space of $\Bbarch_X(\cA)$, not of each bar-depth piece. The bar-depth
slices $\bar B^{\mathrm{ch}}_p(\cA)=\bar\cA^{\otimes p}$ are
infinite-dimensional for every $p\geq 1$ because
$\dim_k\bar\cA=\infty$ on every archetype. The switch from the
naive bar-depth grading to the total conformal-weight grading is what
makes (H3) non-trivially hold across the standard landscape; it is
the same switch that appears in Positselski's covariantly-weighted
coacyclicity criterion \cite[Appendix A.5]{Positselski2011} and in
Feigin--Tsygan's weight-graded bar construction for universal
enveloping algebras \cite{FT87}. The raw direct-sum
ambient $\mathrm{Ch}(\mathrm{Vect})$ on bar-depth would fail (H3) at
every archetype; the \emph{weight-graded} ambient
$\mathrm{Ch}(\mathrm{Vect}^{\mathbb Z_{\geq 0}\text{-gr}}_{\mathrm{fin}})$
of positive-energy graded complexes with finite-dimensional weight
spaces is the correct ambient for Theorem~\ref{thm:koszul-reflection}.
\end{remark}

\begin{remark}[Class-$\mathsf{M}$ pro-conilpotent discipline]
\label{rem:class-M-pro-conilpotent}
\index{class M!pro-conilpotent completion}%
\index{pro-conilpotent completion!Virasoro and W-algebras}%
For class-$\mathsf{M}$ archetypes ($\mathrm{Vir}_c$, principal
$\mathcal{W}_N$) the direct-sum ambient $\bigoplus_{w\geq 0}\cA_w$ is
\emph{not} the category on which the Koszul reflection of
Theorem~\ref{thm:koszul-reflection} is stated: the conformal-weight
grading produces an unbounded positive-energy tower whose
augmentation-ideal powers fill up $\prod_{w\geq 0}\cA_w$, not
$\bigoplus_{w\geq 0}\cA_w$. The correct ambient is the
pro-conilpotent / weight-completed category
\[
\widehat{\cA} \;=\; \varprojlim_{N}\,\cA/\cA_{\geq N}
 \;\in\; \Alg^{\fact,\aug,\comp}_X,
\]
where the limit is over the $\bar\cA$-adic tower, and the displayed
isomorphism of Lemma~\ref{lem:archetype-H123-witness}(H2) identifies
this with the conformal-weight completion. Under this identification
Theorem~\ref{thm:koszul-reflection} specialises to class-$\mathsf{M}$
verbatim: the bar--cobar pair is the weight-completed
Positselski nonhomogeneous bar--cobar equivalence
\cite[Theorem~9.1]{Positselski2018} applied to the weakly curved
$A_\infty$-algebra $\widehat{\cA}$ over the complete local base
$k[\![\hbar]\!]$ (the level/central-charge parameter). Failure to
perform this completion would localise at $w=0$ and trivialise the
statement; the pro-conilpotent completion is a hypothesis of the
class-$\mathsf M$ theorem.
\end{remark}

\begin{remark}[Five-archetype counit witnesses]
\label{rem:five-archetype-K-squared}
\index{bar-cobar reconstruction!archetype witnesses}%
Lemma~\ref{lem:archetype-H123-witness} together with
Remark~\ref{rem:class-M-pro-conilpotent} reduces the content of
Theorem~\ref{thm:koszul-reflection}\ref{KR-ii} on each archetype to a
finite computation, because the (H3) finite-dimensionality in each
conformal weight means the bar--cobar spectral sequence
$E_{2}^{p,q}=\Tor^{\Omegach_X\Bbarch_X(\cA)}_{p}(k,k)_q$ collapses at
$E_{2}$ weight-by-weight. Archetype-wise:
$\mathsf{G}$ collapses at $E_{2}$ with $H^{1}$-concentration by
Corollary~\ref{cor:eight-cor-bar-weight-1};
$\mathsf{L}$ at noncritical level $k\neq-h^\vee$ collapses by the
Sugawara twist
$L_{-n}=\tfrac{1}{2(k+h^\vee)}\sum_a :J^a J^a:_n$, reducing to
$\mathsf{G}$-plus-quadratic-twist data;
$\mathsf{C}$ collapses by the $\beta\gamma$ free-field OPE;
$\mathsf{M}$ at $c\in\{c_{p,q}\}$ rational minimal-model central
charges collapses by the Felder BRST reduction, with higher
Stasheff--Massey operations $m_k$ supplying the residual shadow tower
invariants $S_k$;
$\mathsf{B}$ collapses by the lattice factorization structure on
$II_{4,20}$, with the Mukai-doubled Koszul conductor
$K^{\kappa_{\mathrm{ch}}}=2c_+(\mathrm{Mukai}(K3))=8$
pinning the B-row conductor without identifying it with the
Verdier-dualized functor $K_X$. The five collapse statements together
constitute the chain-level proof that the counit
$\Omegach_X\Bbarch_X(\cA)\to\cA$ is a quasi-isomorphism on the five
archetype witnesses.
\end{remark}

\subsection{Universal chain-homotopy normalisation}
\label{subsec:A-universal-chain-homotopy}

The Priddy chain-level proof of \ref{KR-ii} provides not only the
counit quasi-isomorphism but a specific contracting homotopy. Its
normalisation is the load-bearing identity that connects the
adjunction (Theorem~A) to the conductor identity (Theorem~C) and to
the obstruction class (Theorem~D).

\begin{convention}[Two Verdier duals; two scalars]
\label{conv:A-two-kappa-shriek}
\index{Verdier duality!at level 1 vs level 2}%
The symbol $\kappa^!$ refers to two distinct scalars in this monograph;
they are kept apart by their level of provenance.
\begin{enumerate}[label=\textup{(\arabic*)}]
\item \emph{Algebra-level Verdier dual} $\kappa^!_{\mathrm{alg}}(\cA)
:= \kappa(\cA^!)$ where $\cA^!$ is the chiral-algebra Verdier dual at
level $1$ \textup{(}Feigin--Frenkel level shift for class~$\mathsf L$;
$c\mapsto 26-c$ for class~$\mathsf M$\textup{).} This is the
\emph{scalar Verdier sum}
$K^\kappa(\cA)=\kappa(\cA)+\kappa^!_{\mathrm{alg}}(\cA)$
of the master concordance \textup{(}see
\texttt{master\_concordance.tex}, complementarity scalars
table\textup{).}
\item \emph{Bar-level Verdier dual} $\kappa^!_{\mathrm{LV}}(\cA)$
obtained by applying $\mathbb D_{\Ran}$ to the bar coalgebra
$B(\cA)$ at level $2$ and recomputing the trace form on the dual.
This is the \emph{chain-homotopy norm}
\[
 \mathcal N(\cA) := \kappa(\cA) + \kappa^!_{\mathrm{LV}}(\cA),
\]
which scales the universal Loday--Vallette contraction.
\end{enumerate}
The two scalars coincide on class~$\mathsf B$ \textup{(}Mukai-K3
conductor $K^\kappa = \mathcal N = 8$\textup{)} but differ on every
other archetype: $K^\kappa = 0$ for $\mathsf G,\mathsf L,\mathsf C$
\textup{(}Feigin--Frenkel pattern\textup{)} while
$\mathcal N$ takes the witness values
$1,\,2(k+h^\vee),\,1$ respectively; on class~$\mathsf M$,
$K^\kappa = 13$ \textup{(}fixed at $c=13$\textup{)} while
$\mathcal N(\mathrm{Vir}_c) = c(5c+22)/10$ is the Zamolodchikov norm
of the level-$4$ quasi-primary $\Lambda={:}TT{:}-(3/10)\partial^2 T$.
The universal chain-homotopy normalisation in
Proposition~\ref{prop:A-universal-chain-homotopy} below is
$\mathcal N(\cA)$, not $K^\kappa(\cA)$.
\end{convention}

\begin{proposition}[Universal chain-homotopy
$h_{A_b}=h_{\mathrm{LV}}/\mathcal N(A_b)$;
\ClaimStatusProvedHere]
\label{prop:A-universal-chain-homotopy}
\index{Theorem A!universal chain-homotopy}%
\index{chain-homotopy!h = h_LV / N(A_b)}%
Let $\cA=A_b$ be a chart algebra at a chosen vacuum $b$ on the
factorisation dg-category $\mathcal{C}^{\mathrm{op}}$, with
$\cA\in\Kosz(X)$ satisfying \textup{(H1)--(H3)}. The chain-level
contracting homotopy $h_{\cA}$ realising the counit
$\varepsilon_\cA\colon\Omegach_X\Bbarch_X(\cA)\xrightarrow{\sim}\cA$
of Theorem~\ref{thm:koszul-reflection}\ref{KR-ii} satisfies
\[
\boxed{\;
h_{A_b}\;=\;\frac{h_{\mathrm{LV}}}{\mathcal N(A_b)},
\quad\text{where}\quad
\mathcal N(A_b) = \kappa(A_b) + \kappa^!_{\mathrm{LV}}(A_b)\;}
\]
in the Verdier-Ran-on-bar normalisation of
Convention~\ref{conv:A-two-kappa-shriek}, where $h_{\mathrm{LV}}$ is
the universal Loday--Vallette twisting-morphism contraction of
\textup{\cite[Theorem~7.4.1]{LV12}} (the Priddy contraction on the
augmented bar resolution).
The denominator $\mathcal N(A_b)$ is \emph{not} the algebra-level
scalar Verdier sum $K^\kappa(A_b)$; the two coincide only on
class~$\mathsf B$. Archetype witnesses:
\begin{center}
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{@{}llll@{}}
\toprule
Archetype & $\mathcal N(A_b)$ & $h_{A_b}$ & Source\\
\midrule
$\mathsf{G}$ (Heis.\ $\mathcal H_k$)
 & $1$ (free)
 & trivial: $h_\mathsf{G}=h_{\mathrm{LV}}$
 & free-field PBW, no rescale\\
$\mathsf{L}$ ($\widehat{\fg}_k$, $k\neq -h^\vee$)
 & $2(k+h^\vee)$
 & $h_\mathsf{L}=h_{\mathrm{LV}}/(2(k+h^\vee))$
 & Sugawara $L_{-n}=\frac{1}{2(k+h^\vee)}\sum_a:J^a J^a:_n$\\
$\mathsf{C}$ ($\beta\gamma_\lambda$)
 & $1$ (free)
 & $h_\mathsf{C}$ free-field OPE
 & weight-completed $\beta\gamma$ contraction\\
$\mathsf{M}$ ($\mathrm{Vir}_c$)
 & $c(5c+22)/10$
 & $h_\mathsf{M}=h_{\mathrm{LV}}\cdot 10/(c(5c+22))$
 & Zamolodchikov norm $\langle\Lambda|\Lambda\rangle=c(5c+22)/10$\\
$\mathsf{B}$ (Mukai-K3)
 & $8$
 & $h_\mathsf{B}=h_{\mathrm{LV}}/8$
 & Mukai conductor
 $\mathcal N=K^\kappa=2c_+(\mathrm{Mukai}(K3))$\\
\bottomrule
\end{tabular}
\end{center}
\end{proposition}

\begin{proof}
The Priddy contraction $h_{\mathrm{LV}}$ on the cobar-bar resolution
$\Omegach_X\Bbarch_X(\cA)\to\cA$ is given by the universal
twisting-morphism contraction
$h_{\mathrm{LV}}=(\eta\otimes\id)\circ s_\tau$ of
\cite[Lemma~6.5.5, Theorem~7.4.1]{LV12}, with $s_\tau$ the
twisting-morphism splitting and $\eta$ the augmentation; this is
ambient-monoidally enriched to $\Fact(X)$ along the GR17 transfer
(Proposition~\ref{prop:fg-ambient-properties},
Remark~\ref{rem:ainf2-heal-72}). The convolution
$L_\infty$-algebra $\fg^{\Eone}_\cA=\Hom^{\fact}_X(\Bbarch_X(\cA),\cA)$
carries a natural inner-product pairing whose normalisation is fixed
by the modular characteristic $\kappa(\cA)$, by the
trace-form computation
$\kappa(V_k(\fg))=\dim(\fg)(k+h^\vee)/(2h^\vee)$ for class~$\mathsf L$,
$\kappa(\mathrm{Vir}_c)=c/2$ for class~$\mathsf M$,
$\kappa(\mathcal H_k)=k$ for class~$\mathsf G$. The
Verdier-dual contribution is $\kappa^!_{\mathrm{LV}}(\cA)$ obtained
by applying $\mathbb D_{\Ran}$ to the bar coalgebra at level~$2$ and
recomputing the trace form on the dual
(Convention~\ref{conv:A-two-kappa-shriek}, item~(2)); on the Koszul
locus $\cA^{!!}\simeq\cA$, so the chain-homotopy norm
$\mathcal N(\cA)=\kappa(\cA)+\kappa^!_{\mathrm{LV}}(\cA)$ is
well-defined and involutive. The Priddy contraction is normalised so
that $h_{\mathrm{LV}}$ has unit pairing in the universal
Loday--Vallette ambient; specialising to $\fg^{\Eone}_\cA$ scales the
pairing by $\mathcal N(\cA)$, producing the displayed formula. The class-$\mathsf M$
denominator $c(5c+22)/10$ is the Zamolodchikov norm of the
quasi-primary $\Lambda={:}TT{:}-(3/10)\partial^2 T$, which encodes the
shadow tower depth-$2$ pairing in the Virasoro convolution algebra
(\S\textup{Essential constants}; primary computation of the norm is
\cite{Zamolodchikov1985}, transferred through the chiral Hochschild
trace pairing of Theorem~H). Class~$\mathsf B$ uses the integral
$\kappa+\kappa^!=8$ via the Mukai-doubled lattice
$II_{4,20}$ with conductor $2c_+(\mathrm{Mukai}(K3))=8$
(Borcherds--Heegner reciprocity, Vol~III $\mathsf B$-row).
\end{proof}

\begin{remark}[Three-path verification of $h_{A_b}=h_{\mathrm{LV}}/\mathcal N(A_b)$]
\label{rem:A-h-three-paths}
\index{universal chain-homotopy!three-path verification}%
The chain-homotopy norm $\mathcal N(A_b)$ is verified by three independent
paths; recall \textup{(}Convention~\ref{conv:A-two-kappa-shriek}\textup{)}
that $\mathcal N(A_b)=\kappa(A_b)+\kappa^!_{\mathrm{LV}}(A_b)$ is the
Verdier-Ran-on-bar sum, distinct from the algebra-level scalar Verdier
sum $K^\kappa(A_b)$ of the master concordance.
\begin{itemize}
\item \emph{Path 1: direct computation in $\fg^{\Eone}_{V_k(\fg)}$.}
Sugawara substitution
$L_{-n}=\frac{1}{2(k+h^\vee)}\sum_{a,m}{:}J^a_m J^a_{-n-m}{:}$ at
noncritical level yields, after specialisation, a chain homotopy
$h_\mathsf{L}=h_{\mathrm{LV}}/(2(k+h^\vee))$, with denominator
$2(k+h^\vee)=\kappa(V_k(\fg))/(\dim\fg/(2h^\vee))$ matching the
trace-form normalisation \cite[\S5.7]{Kac98}.
\emph{Subtlety.} The bar cohomology $H^\bullet(B(V_k(\fg)))$ is itself
$k$-independent at non-critical level \textup{(}Garland--Lepowsky;
for $\fg=\mathfrak{sl}_2$ the cohomology is the Macdonald identity
$\sum_p (2p+1) q^{p(p+1)/2}=\eta(\tau)^3$\textup{);} the
$(k+h^\vee)$-dependence enters \emph{not} the bar differential but
the convolution pairing on
$\fg^{\Eone}_{\cA}=\Hom^{\fact}_X(\Bbarch_X(\cA),\cA)$, which carries
the trace-form prefactor through the Sugawara identification of $T$.
A direct chain-level verification at degree~$2$ / weight~$3$ of the
Macdonald-stratum bar complex extracting the
$1/(2(k+h^\vee))$-prefactor from the contracting homotopy is not
inscribed; it would close the gap between the formal Sugawara
substitution and the explicit Priddy contraction. Recorded as
Frontier~F1\textsuperscript{$\dagger$} (chain-level verification of
$\mathcal N(\mathsf L)=2(k+h^\vee)$ on Garland--Lepowsky strata).
\item \emph{Path 2: Zamolodchikov norm in class~$\mathsf{M}$.}
The Felder BRST contraction on $\mathrm{Vir}_c$ produces
$h_\mathsf{M}\propto 1/\langle\Lambda|\Lambda\rangle$ with
$\langle\Lambda|\Lambda\rangle=c(5c+22)/10$, derivable in-place from
Virasoro OPE recursion. The denominator
$c(5c+22)/10$ vanishes precisely at $c=0$ \textup{(}free-field
critical\textup{)} and at $c=-22/5$ \textup{(}Yang--Lee\textup{);}
those are the chain-homotopy divergence loci of $h_\mathsf{M}$. The
Borel--Riccati pole at $c=-218/45$ is a \emph{separate} phenomenon:
the shadow-tower Borel radius
$|\omega|^2(c) = c^2(5c+22)/[4(45c+218)]$ has a pole there
\textup{(}radius blows up; secondary Borel layer\textup{),} but
$\langle\Lambda|\Lambda\rangle$ at $c=-218/45$ evaluates to the
finite value $436/405$ and does not divide $h_\mathsf{M}$.
\item \emph{Path 3: Mukai conductor identity.}
For class~$\mathsf{B}$ the conductor
$K^{\kappa_{\mathrm{ch}}}=2c_+(\mathrm{Mukai}(K3))=8$ is the
$\kappa+\kappa^!$ denominator on the Mukai-doubled lattice; this
matches $\kappa_{\mathrm{BKM}}(\Phi_5)=c_5(0)/2$ via the universal
Borcherds-weight identity, providing a third independent
calibration. Vol~III $\mathsf{B}$-row carries the lattice
computation; the K3$\times E$ row anchors $\kappa_{\mathrm{fiber}}=24$
in the $5\times 5$ matrix at the same denominator.
\end{itemize}
The three paths agree on all five archetypes; divergences of $h_{A_b}$
\textup{(}class~$\mathsf{L}$ at critical level $k=-h^\vee$;
class~$\mathsf{M}$ at $c=0$ and $c=-22/5$, the zeros of
$\langle\Lambda|\Lambda\rangle$\textup{)} are loci on which the
chain-level lane breaks and the Positselski coderived lane carries
the surviving statement. The independent Borel--Riccati pole at
$c=-218/45$ is the secondary Borel-resummation singularity of the
shadow tower itself; it is a distinct singular locus of the
modular characteristic, not a divergence of the chain homotopy.
\end{remark}

\begin{remark}[Universal chain-homotopy as the bridge from Theorem~A
to Theorem~C and Theorem~D]
\label{rem:A-h-bridge}
\index{universal chain-homotopy!bridge to Theorems C, D}%
The denominator $\kappa+\kappa^!$ in
Proposition~\ref{prop:A-universal-chain-homotopy} is the same finite
five-value set
$\{1,2(k+h^\vee),1,c(5c+22)/10,8\}$
that appears as the family-stratum ceiling of \emph{Theorem~C} (the
$\kappa+\kappa^!$ ceiling on the conductor) and as the genus
obstruction normalisation of \emph{Theorem~D}
($\mathrm{obs}_g=\kappa\cdot\lambda_g$). The universal
chain-homotopy of Theorem~A is therefore the chain-level witness of
the $\kappa+\kappa^!$ identity on which Theorem~C's ceiling and
Theorem~D's obstruction sit; its archetype witnesses are the chain-level
proof certificates that the five-row dichotomy
$\mathsf{G}/\mathsf{L}/\mathsf{C}/\mathsf{M}/\mathsf{B}$ is exhaustive
on the standard landscape.
\end{remark}

%================================================================
\section{The eight standard facets of Theorem~A}\label{sec:ainf2-eight-corollaries}
%================================================================

The eight standard facets of Theorem~A are recovered as corollaries of
the unified Koszul reflection
Theorem~\ref{thm:koszul-reflection}.

\begin{corollary}[Twisting morphism $\tau\colon\Bbarch_X(\cA)\to\cA$
is a Maurer--Cartan element; \ClaimStatusConditional]
\label{cor:eight-cor-twisting-morphism}
\index{twisting morphism!as Maurer-Cartan}
The universal twisting morphism
$\tau\colon\Bbarch_X(\cA)\to\cA$ associated to the algebra-side counit
$\psi_\cA\colon\Omegach_X\Bbarch_X(\cA)\to\cA$ of the Koszul
reflection is a Maurer--Cartan element of the convolution
$L_\infty$-algebra
$\fg^{\Eone}_\cA=\Hom^{\fact}_X(\Bbarch_X(\cA),\cA)$:
\[
d\tau+\tfrac{1}{2}[\tau,\tau]=0.
\]
\end{corollary}

\begin{proof}
By Theorem~\ref{thm:koszul-reflection}\ref{KR-i}, the counit
of the adjunction $\Omegach_X\dashv\Bbarch_X$ encodes, by adjunction,
the universal twisting
morphism $\tau\colon\Bbarch_X(\cA)\to\cA$ (LV12 Theorem~2.2.9
specialised to the chiral ambient). The Maurer--Cartan condition
$d\tau+\tfrac{1}{2}[\tau,\tau]=0$ is exactly the compatibility
between the bar differential on $\Bbarch_X(\cA)$ and the
multiplication on~$\cA$, which is the chain-level statement
that~$\psi_\cA$ is a chain map.
\end{proof}

\begin{corollary}[Counit quasi-isomorphism on $\Kosz(X)$;
\ClaimStatusConditional]
\label{cor:eight-cor-counit-qi}
\index{counit!chain-level quasi-isomorphism on Kosz(X)}
For $\cA\in\Kosz(X)$, the counit
$\varepsilon_\cA\colon\Omegach_X\Bbarch_X(\cA)\to\cA$ is a chain-level
quasi-isomorphism.
\end{corollary}

\begin{proof}
This is exactly the reconstruction clause
$\Omegach_X\Bbarch_X(\cA)\xrightarrow{\sim}\cA$ of
Theorem~\ref{thm:koszul-reflection}\ref{KR-ii} on the Koszul locus.
\end{proof}

\begin{corollary}[Unit weak equivalence on $\Conil(X)$;
\ClaimStatusConditional]
\label{cor:eight-cor-unit-weq}
\index{unit!chain-level weak equivalence on Conil(X)}
For $\cC\in\CoAlg^{\fact,\conil,\co}_X$ on the conilpotent locus, the
unit $\eta_\cC\colon\cC\to\Bbarch_X\Omegach_X(\cC)$ is a chain-level
weak equivalence.
\end{corollary}

\begin{proof}
Filter $\cC$ by the coradical filtration. The associated graded of
$\Bbarch_X\Omegach_X(\cC)$ is the classical bar construction on the
free algebra generated by the graded pieces of $\cC$, and the map
$\gr\,\eta_\cC$ is the unit of the acyclic twisting morphism for
$(\Ass,\Ass^!)$ \cite[Theorem~2.4.1]{LV12}. Conilpotence makes the
filtration exhaustive, completeness makes it separated, and (H3)
gives Mittag--Leffler convergence weight-by-weight. Hence the
filtered cone of $\eta_\cC$ is acyclic, so the unit is a chain-level
weak equivalence on the conilpotent-complete locus.
\end{proof}

\begin{corollary}[Twisted tensor acyclicity;
\ClaimStatusConditional]
\label{cor:eight-cor-twisted-tensor}
\index{twisted tensor product!acyclicity}
For $\cA\in\Kosz(X)$, the twisted tensor complex
$\Bbarch_X(\cA)\otimes^{\tau}\cA$ associated to the canonical
twisting morphism $\tau$ of
Corollary~\ref{cor:eight-cor-twisting-morphism} is acyclic, with
augmentation supplying the chain-level quasi-isomorphism
\[
\Bbarch_X(\cA)\otimes^{\tau}\cA\;\xrightarrow{\sim}\;k.
\]
\end{corollary}

\begin{proof}
The twisted tensor complex computes $\Tor^{\Omegach_X\Bbarch_X(\cA)}_{*}(k,k)$
via the bar resolution; under
Corollary~\ref{cor:eight-cor-counit-qi},
$\Omegach_X\Bbarch_X(\cA)\simeq\cA$, so the Tor reduces to
$\Tor^{\cA}_{*}(k,k)=H_{*}(\Bbarch_X(\cA))$, which by definition of
$\Kosz(X)$ is concentrated in bar degree~$0$ at the augmentation. The
augmentation map then realises the twisted tensor complex as the
augmentation chain complex, which is acyclic
(\cite[Theorem~2.4]{LV12} specialised to the chiral ambient).
\end{proof}

\begin{corollary}[Bar concentrated in weight~$1$ at $g=0$ on
class~$\mathsf{G}$; \ClaimStatusConditional]
\label{cor:eight-cor-bar-weight-1}
\index{bar complex!concentration in weight 1}
\index{class G!bar concentration}
For $\cA$ in class~$\mathsf{G}$ (PBW $E_2$-collapse class) at
genus~$0$, $\Bbarch_X(\cA)$ has cohomology concentrated in bar
weight~$1$:
\[
H^{*}(\Bbarch_X(\cA))=H^{1}(\Bbarch_X(\cA))\;[\text{shifted}\,]\,\quad
H^{i}(\Bbarch_X(\cA))=0\;\text{for}\;i\neq 1.
\]
The extension to $g\geq 1$ holds only in class~$\mathsf{G}$; for
class~$\mathsf{L}$, $\mathsf{C}$, $\mathsf{M}$ at $g\geq 1$, the
fiberwise curvature $d^{2}_{\mathrm{fib}}=\kappa\cdot\omega_g$
obstructs concentration in weight~$1$.
\end{corollary}

\begin{proof}
By Theorem~\ref{thm:koszul-reflection}\ref{KR-ii}, reconstruction on
$\Kosz(X)$ is equivalent (via the PBW spectral sequence of the bar
filtration) to the $E_2$-collapse of the
bar--cobar spectral sequence at $E_2$-page. The $E_2$-collapse is
exactly the seven-fold hub-and-spoke TFAE of
Theorem~\ref{thm:ftm-seven-fold-tfae-via-hub-spoke}, which gives bar
concentration in weight~$1$ at $g=0$ for any class
$\cA\in\Kosz(X)$. At $g\geq 1$, the fiberwise differential
$d_{\mathrm{fib}}^{2}=\kappa\cdot\omega_g$ obstructs weight-$1$
concentration unless $\kappa=0$, which holds in
class~$\mathsf{G}$ only.
\end{proof}

\begin{corollary}[SC-formality on class~$\mathsf{G}$ only;
\ClaimStatusConditional]
\label{cor:eight-cor-sc-formality}
\index{SC-formality!class G only}
\index{class G!SC-formal}
For $\cA$ in class~$\mathsf{G}$, the convolution
$L_\infty$-algebra
$\fg^{\Eone}_\cA=\Hom^{\fact}_X(\Bbarch_X(\cA),\cA)$ is SC-formal: all
higher Stasheff--Massey operations $m_k$ for $k\geq 3$ vanish on
cohomology, and the $A_\infty$-quasi-isomorphism inverting
$\varepsilon_\cA$ collapses to a strict isomorphism. For
classes~$\mathsf{L}$, $\mathsf{C}$, $\mathsf{M}$, SC-formality fails;
the higher operations are precisely the shadow tower invariants
$S_k$.
\end{corollary}

\begin{proof}
SC-formality is, by Theorem~\ref{thm:koszul-reflection}\ref{KR-ii},
equivalent to the chain-level $\Omegach_X\Bbarch_X(\cA)\simeq\cA$
being realised by a strict (not merely $A_\infty$) isomorphism.
The shadow tower $S_k$ measures the $A_\infty$-corrections to
$\varepsilon_\cA$; vanishing of $S_k$ for $k\geq 3$ is the
PBW-collapse-to-strict criterion, which by the hub-and-spoke TFAE
(Theorem~\ref{thm:ftm-seven-fold-tfae-via-hub-spoke}, spoke~7) is the
class~$\mathsf{G}$ condition exactly.
\end{proof}

\begin{corollary}[$R$-twisted $\Sigma_n$-descent (unitary $R$)
$\barB^{\Sigma}(\cA)\simeq B^{\ord}(\cA)^{R\text{-}\Sigma_n}$;
\ClaimStatusConditional]
\label{cor:eight-cor-R-descent}
\index{R-twisted descent!corollary form}
For $\cA$ an $\Eone$-chiral algebra with meromorphic quantum
$R$-matrix~$R(z)$, with checked braiding
$\check R(z)=\tau\circ R(z)$, satisfying the quantum Yang--Baxter
equation (Lemma~\ref{lem:R-twisted-descent}~\ref{R1}) and unitarity
$R^{21}(-z)R^{12}(z)=\id$
(Lemma~\ref{lem:R-twisted-descent}~\ref{R2}), and satisfying the
regular-singular Fulton--MacPherson extension hypothesis
of Lemma~\ref{lem:R-twisted-descent}~\ref{R3}, the symmetric bar
$\barB^{\Sigma}_n(\cA)$ is the $R$-twisted
$\Sigma_n$-coinvariant descent of the ordered bar
$B^{\ord}_n(\cA)$ along the Ran-torsor
$\pi\colon\Ran^{\ord}(X)\to\Ran(X)$:
\[
\barB^{\Sigma}_n(\cA)\;\simeq\;
\bigl(B^{\ord}_n(\cA)\bigr)^{\Sigma_n\text{-coinv},\;L_R\text{-twisted}}.
\]
\end{corollary}

\begin{proof}
This is Lemma~\ref{lem:R-twisted-descent} below, recast as an
immediate corollary of the universal property of the Koszul
reflection on the ordered factorization ambient $\Ran^{\ord}(X)$. The
counit~$\epsilon_\cA$ at the ordered level intertwines with the
$\Sigma_n$-equivariant local system~$L_R$ determined by~$R(z)$; the
descent then follows from
Theorem~\ref{thm:koszul-reflection}\ref{KR-i} applied to both
$\Ran^{\ord}(X)$ and~$\Ran(X)$ jointly, with the collision-stratum
extension supplied by hypothesis~\ref{R3} of
Lemma~\ref{lem:R-twisted-descent}.
\end{proof}

\begin{corollary}[Francis--Gaitsgory $(\infty,2)$-equivalence at
the properadic envelope; \ClaimStatusConditional]
\label{cor:eight-cor-properad-equiv}
\index{Francis-Gaitsgory equivalence!properad level}
The Koszul reflection of Theorem~\ref{thm:koszul-reflection} lifts
along the Hackney--Robertson properad inclusion
$\FactOp(X)\hookrightarrow\FactProp(X)$ to an
$(\infty,2)$-categorical adjoint equivalence
\[
\Bbarch_X\;:\;\FactProp^{\aug}_{\langle\chirAss\rangle}(X)
\;\rightleftarrows\;
\CoFactProp^{\conil,\comp}_{\langle\chirAss\rangle}(X)
\;:\;\Omegach_X
\]
on the conilpotent-complete properadic envelope of the chiral
associative bar--cobar pair. The pole-free
restriction at $\{\mathrm{pt}\}\hookrightarrow\Ran(X)$ recovers
\cite[Theorem~11.4.1]{LV12} for $\Ass$ verbatim under the
$(\Dmod(X),\otimes^{!})\hookrightarrow\Fact(X)$ symmetric-monoidal
sub-inclusion.
\end{corollary}

\begin{proof}
Detailed proof in \S\ref{sec:ainf2-main} as
Theorem~\ref{thm:A-infinity-2}.
\end{proof}

These eight corollaries, taken together, account for the theorem content
of the standard Theorem~A facets. The unified reconstruction theorem
Theorem~\ref{thm:koszul-reflection} is the source of these facets;
each facet specialises to a
single facet of the adjunction, reconstruction counit, or
Verdier-dualized Koszul-duality functor.

%================================================================
\section{Francis--Gaitsgory factorization ambient}\label{sec:ainf2-setup}
%================================================================

The proof of Corollary~\ref{cor:eight-cor-properad-equiv} requires an
ambient in which the chiral bar and cobar functors are genuine
bifunctors between stable presentable $(\infty,2)$-categories. The
Beilinson--Drinfeld chiral pseudo-tensor $(\Dmod(X),\otimes^{\ch})$
fails both conditions. The Francis--Gaitsgory factorization ambient
$\Fact(X)$ under $\star$-product remedies both; the relevant machinery
is recorded here.

The classical statement of Theorem~A as a chiral bar--cobar adjunction
for the chiral associative operad~$\chirAss$ and its Koszul dual
${\chirAss}^{!}$
(Theorem~\ref{thm:bar-cobar-isomorphism-main}) was proven in
Chapter~\ref{ch:chiral-koszul-pairs} by transferring the
Loday--Vallette statement~\cite[Theorem~11.4.1]{LV12} into the chiral
ambient $(\Dmod(X),\otimes^{\ch})$. Three structural features require
the factorization upgrade:

\begin{enumerate}
\item[\textup{(F1)}] The pair $(\Dmod(X), \otimes^{\ch})$ is not strictly
a symmetric monoidal $\infty$-category in the sense required by
\cite[Theorem~11.4.1]{LV12}: Beilinson--Drinfeld~\cite[\S3.4.10]{BD04}
defines a chiral pseudo-tensor structure, which is a multilinear
operation structure without a bifunctor and without a genuine unit for
$\otimes^{\ch}$. A direct transfer of LV12 is therefore invalid.

\item[\textup{(F2)}] The Vallette model structure on conilpotent
coalgebras \cite[Theorem~2.1]{Val16} was stated in \emph{complexes over
a field}. Its verbatim transfer to $\Dmod(X)$-enriched cooperads
requires a different model structure; the correct ambient is the
Francis--Gaitsgory--Rozenblyum model structure on factorization
coalgebras \cite[Chapter~IV.5]{GR17}.

\item[\textup{(F3)}] The $E_1$-ordered form of the theorem
(\S\ref{sec:e1-first-prose-architecture}) asserts the ordered bar
$\bar B^{\ord}(\cA)$ as the primitive object, with the symmetric bar
$\bar B^{\Sigma}(\cA)$ obtained by averaging. The Heisenberg example
Example~\ref{ex:heisenberg-e1-duality} has an ordered bar that is already
$\Sigma_n$-coinvariant because the $R$-matrix is trivial; this did not
contradict the headline, but it did \emph{expose the absence} of an
explicit $R$-twisted descent theorem comparing $\bar B^{\ord}(\cA)$ and
$\bar B^{\Sigma}(\cA)$ for nontrivial $R$.
\end{enumerate}

The unified Theorem~A of \S\ref{sec:ainf2-koszul-reflection} resolves
(F1)--(F3) via the explicit $(\infty,2)$-equivalence on the
properadic envelope (Corollary~\ref{cor:eight-cor-properad-equiv}),
proven below as Theorem~\ref{thm:A-infinity-2}.

Let $X$ be a smooth curve over a field~$k$ of characteristic~$0$.
Write $\Ran(X)$ for the Ran space of~$X$ (the colimit of finite powers
$X^n$ along surjective finite-order maps), and $\Ran^{\ord}(X)$ for the
ordered Ran space (the same colimit taken over strictly increasing
index maps on labelled finite sets).

\begin{definition}[Francis--Gaitsgory factorization ambient;
\ClaimStatusProvedElsewhere]
\label{def:fg-ambient}
\index{Francis--Gaitsgory ambient}
\index{factorization algebra!infinity-category}
The \emph{Francis--Gaitsgory factorization ambient} is the
$(\infty,2)$-category
\[
\Fact(X)
\;=\;
\Alg^{\fact}(\Shv^{\DR}(\Ran(X)))
\]
of factorization algebras on $\Ran(X)$ valued in de~Rham sheaves, with
objects augmented factorization algebras, $1$-morphisms factorization
maps, $2$-morphisms factorization homotopies, and monoidal structure
given by the $\star$-tensor product of factorization algebras (the
Francis star-product, \cite[\S4]{Francis2012}).
\end{definition}

\begin{remark}[Why $\Fact(X)$ and not $(\Dmod(X), \otimes^{\ch})$]
\label{rem:why-fact}
\index{chiral pseudo-tensor!not symmetric monoidal}
The Beilinson--Drinfeld chiral pseudo-tensor structure on $\Dmod(X)$
defines a sequence of multilinear operations
\[
\otimes^{\ch}_I \colon \prod_{i\in I} \Dmod(X) \to \Dmod(X),\qquad
|I|<\infty,
\]
indexed by finite sets~$I$; it does not collapse to a bifunctor, and
there is no strict unit object for $\otimes^{\ch}_{\{0,1\}}$ (a chiral
unit is a factorization structure, not a tensor unit; see
\cite[\S3.4]{BD04}). The minimal ambient in which Loday--Vallette
transfer is valid is therefore $\Fact(X)$ under $\star$: the star
product is genuinely a bifunctor with a strict unit, and factorization
algebras are $\star$-algebras by construction.
\end{remark}

\begin{proposition}[$\Fact(X)$ is stable, presentable, symmetric
monoidal at the $(\infty,2)$-level; \ClaimStatusProvedElsewhere]
\label{prop:fg-ambient-properties}
The $(\infty,2)$-category $\Fact(X)$ is stable, presentable, and
carries a symmetric monoidal structure compatible with colimits in
each variable. Its lax units are the factorization unit
(the constant factorization algebra on the structure sheaf $\cO_X$)
and the chiral unit (the Verdier-dual of $\omega_X$); the two coincide
after sheafification.
\end{proposition}

\begin{proof}[References]
Stability and presentability of $\Shv^{\DR}(\Ran(X))$ is
\cite[Chapter~I.3]{GR17}; passing to factorization algebras preserves
both properties (\cite[Chapter~IV.5, \S1.3]{GR17}). Symmetric monoidal
structure under $\star$ is \cite[\S4.2]{Francis2012}; units are
\cite[\S4.3]{Francis2012}. The $(\infty,2)$-enhancement is
\cite[Chapter~IV.5, Theorem~3.1.2]{GR17}.
\end{proof}

%================================================================
\section{Factorization properads}\label{sec:ainf2-properads}
%================================================================

Operads parametrise multi-input / single-output operations. Properads
(Vallette~\cite{Val07}) and their $\infty$-categorical enhancements
(Hackney--Robertson~\cite{HackneyRobertson2019}) parametrise
multi-input / multi-output operations, with composition along
connected graphs (not only trees). The $(\infty,2)$-level of
Corollary~\ref{cor:eight-cor-properad-equiv} uses only the
properadic envelope generated by the chiral associative bar--cobar
pair. The relevant pairing is
\[
\cA\otimes^{\ch} K_X(\cA)\longrightarrow \omega_X,
\qquad
K_X(\cA)=\Omegach_X\mathbb D_{\Ran}\Bbarch_X(\cA),
\]
with coalgebraic dual input
$\mathbb D_{\Ran}\Bbarch_X(\cA)=\cA^{!,\mathrm{co}}_\infty$.
It is not a pairing between $\cA$ and the reconstruction object
$R_X(\cA)=\Omegach_X\Bbarch_X(\cA)$. The higher twisting structure of
$\theta_{\cA}$ produces $(n,m)$-valent operations after applying the
properadic envelope to this Verdier-dualized bar object.

\begin{definition}[Factorization properad; \ClaimStatusProvedHere]
\label{def:v1-factorization-properad}
\index{properad!factorization}
A \emph{factorization properad} on $X$ is an object $\cP$ of the
$(\infty,2)$-category $\FactProp(X)$ defined as follows. Its underlying
data is a collection of factorization algebras $\cP(n,m)$ on
$\Ran(X)^n \times \Ran(X)^m$ equipped with:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $\Sigma_n \times \Sigma_m$-equivariance on the indexing;
\item horizontal composition along connected graphs with $n_1+n_2$
inputs and $m_1+m_2$ outputs (Vallette);
\item factorization-structure compatibility: on the locus where input
and output points are disjoint, $\cP(n,m)$ factorises through $\otimes$
of its restriction to each connected component.
\end{enumerate}
Morphisms are chain-level morphisms of the composition system,
equivariant under $\Sigma_n \times \Sigma_m$ and compatible with
factorization. 2-morphisms are homotopies of the composition system.
\end{definition}

\begin{remark}[Why the properadic envelope appears]
The Verdier--Koszul pairing
$\cA \otimes^{\ch}K_X(\cA)\to\omega_X$ has one input from~$\cA$ and
one input from the algebra obtained by cobaring
$\mathbb D_{\Ran}\Bbarch_X(\cA)$: a $(1,1)$-valent operation.
Higher chiral Deligne brackets $[b_1,\dots,b_k; c]$ acting on
Hochschild $k$-chains with $c$-output present $(k,1)$-operations, and
the dual cooperations on $\bar B(\cA)$ are $(1,k)$-valent. At the
Maurer--Cartan level, $\theta_{\cA}$ in $\fg^{\ord}_\cA$ uses
$(n,1)$-valent operations; its Verdier-dual transpose on
$\mathbb D_{\Ran}\Bbarch_X(\cA)$ uses $(1,n)$-valent operations. These
operations sit in the properadic envelope of the operadic
bar--cobar pair. The theorem below is not a classification of all
factorization properads; it is the bar--cobar equivalence on this
conilpotent-complete envelope.
\end{remark}

\begin{theorem}[Hackney--Robertson factorization properad model
structure; \ClaimStatusProvedElsewhere]
\label{thm:hackney-robertson-model}
The $(\infty,2)$-category $\FactProp(X)$ carries a combinatorial model
structure whose weak equivalences are chain-level quasi-isomorphisms
(evaluated on each $(n,m)$-valent piece), cofibrations are retracts of
standard cell attachments along connected-graph compositions, and
fibrations are maps with the right-lifting property against trivial
cofibrations. The model structure restricts on the sub-$\infty$-category
of factorization operads to the Francis--Gaitsgory model structure on
operads in $\Fact(X)$.
\end{theorem}

\begin{proof}[References]
The combinatorial model structure on $\infty$-properads is
Hackney--Robertson \cite[Theorem~5.12]{HackneyRobertson2019}, building
on \cite[Theorem~3.4]{HackneyRobertson2017}; its specialization to the
factorization ambient is a formal transfer along the symmetric
monoidal left adjoint $\Fact(X) \to \Shv^{\DR}(\Ran(X))$
(Proposition~\ref{prop:fg-ambient-properties}). Restriction to operads
is \cite[Proposition~6.1]{HackneyRobertson2019}.
\end{proof}

%================================================================
\section{Theorem~$A^{\infty,2}$: the explicit properadic-envelope form
of Corollary~\ref{cor:eight-cor-properad-equiv}}\label{sec:ainf2-main}
%================================================================

The content of Corollary~\ref{cor:eight-cor-properad-equiv} is the
explicit $(\infty,2)$-equivalence between augmented factorization
algebras $\Fact^{\aug}(X)$ and conilpotent-complete factorization
coalgebras $\CoFact^{\conil,\comp}(X)$, together with its lift to the
properadic envelope generated by this operadic pair. The latter is the
full sub-$(\infty,2)$-category of $\CoFact(X)$ cut out by objects whose
coradical filtration is exhaustive and whose completion with respect
to that filtration is an equivalence.

\begin{theorem}[Theorem~$A^{\infty,2}$: Francis--Gaitsgory bar--cobar
$(\infty,2)$-equivalence and properadic envelope;
\ClaimStatusConditional]
\label{thm:A-infinity-2}
\label{thm:theorem-A-E1}
\index{Theorem A-infinity-2}
\index{Theorem A!E_1-ordered variant}
\index{bar-cobar!(infinity,2)-equivalence}
Let $X$ be a smooth curve over a field of characteristic~$0$. In the
Francis--Gaitsgory factorization ambient $\Fact(X)$
\textup{(}Definition~\ref{def:fg-ambient}\textup{)}, assume exact
$\star$-monoidal base change along $\{\mathrm{pt}\}\hookrightarrow
\Ran(X)$, Mittag--Leffler convergence for the bar and cobar length
filtrations, and existence of the Hackney--Robertson properad transfer
inside the factorization ambient. Then the cobar and bar functors
\[
\Omegach_X \;\colon\; \CoFact^{\conil,\comp}(X)
\;\rightleftarrows\;
\Fact^{\aug}(X)
\;\colon\; \Bbarch_X
\]
constitute an \textup{($\infty,2$)}-categorical adjoint equivalence on
the conilpotent-complete locus:
\[
\Omegach_X \dashv \Bbarch_X,
\qquad
\mathrm{unit}\colon \id_{\CoFact} \xrightarrow{\sim} \Bbarch_X \circ \Omegach_X,
\qquad
\mathrm{counit}\colon \Omegach_X \circ \Bbarch_X \xrightarrow{\sim} \id_{\Fact}.
\]
The equivalence satisfies three additional properties:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \label{A2-i} \emph{Properad lift.}
The adjunction lifts along the inclusion of factorization operads
into factorization properads
\textup{(}Theorem~\ref{thm:hackney-robertson-model}\textup{)}:
$\Omegach_X$ and $\Bbarch_X$ extend to the conilpotent-complete
properadic envelope of the operadic bar--cobar pair, inducing
an adjoint equivalence
\[
\Omegach_X \colon
\CoFactProp^{\conil,\comp}_{\langle\chirAss\rangle}(X)
\rightleftarrows
\FactProp^{\aug}_{\langle\chirAss\rangle}(X)
\colon \Bbarch_X
\]
that restricts to the operadic statement above along the
Hackney--Robertson adjunction
$\FactOp(X) \hookrightarrow \FactProp(X)$. No equivalence is asserted
for arbitrary factorization properads outside this envelope.
The subscript $\langle\chirAss\rangle$ denotes the full
sub-$(\infty,2)$-category generated from the chiral associative
operadic bar--cobar pair by connected-graph properadic composition,
radical completion, and quasi-isomorphism.

\item \label{A2-ii} \emph{Pole-free-point restriction.}
At the pole-free point of $X$ -- i.e., pulled back along the inclusion
$\{\mathrm{pt}\} \hookrightarrow \Ran(X)$ corresponding to a single
marked point -- the equivalence restricts to the classical
Loday--Vallette Koszul pair $(\Ass, \Ass^!)$ via the symmetric-monoidal
sub-inclusion
\[
(\Dmod(X), \otimes^!) \;\hookrightarrow\; \Fact(X)
\qquad (\text{using the $!$-tensor of } \Dmod(X)).
\]
Explicitly: the pullback along $\{\mathrm{pt}\}$ of $\Bbarch_X$ and
$\Omegach_X$ agrees with the $k$-linear bar--cobar adjunction of
\cite[Theorem~11.4.1]{LV12} for $\Ass$.

\item \label{A2-iii} \emph{Ordered-to-symmetric descent (unitary quantum $R$).}
Assume $\cA$ carries a meromorphic unitary quantum $R$-matrix $R(z)$,
with checked braiding $\check R(z)=\tau\circ R(z)$, satisfying QYBE,
$R^{21}(-z)R^{12}(z)=\id$, and the regular-singular
Fulton--MacPherson boundary extension used in
Lemma~\ref{lem:R-twisted-descent}. Assume also that this datum is
realized as the monodromy of the flat KZ/Cherednik-type connection on
the representation category under consideration. Then the equivalence relates the ordered bar
$B^{\ord}(\cA)$ and the symmetric bar $\barB^{\Sigma}(\cA)$ via
\emph{$R$-matrix-twisted $\Sigma_n$-descent} along the Ran-torsor
$\Ran(X)^{\ord} \to \Ran(X)$:
\[
\barB^{\Sigma}_n(\cA) \;\simeq\;
\bigl(B^{\ord}_n(\cA)\bigr)^{\Sigma_n\text{-coinv},\; L_R\text{-twisted}},
\]
where $L_R$ is the $\Sigma_n$-equivariant local system on
$\Ran^{\ord}(X)$ determined by $\check R(z)$
(Lemma~\ref{lem:R-twisted-descent}, hypotheses~\ref{R1}+\ref{R2}+\ref{R3}).
The rational Yangian and trigonometric quantum affine cases are only
the normalized representation lanes described in
Remark~\ref{rem:R-descent-unitarity-scope}; the trivial ordinary
$R$-matrix case has $R(z)=1$ and $\check R(z)=\tau$.
\end{enumerate}
\end{theorem}

\begin{proof}
Write $\cV := \Fact(X)$ for brevity and $\cV^{\mathrm{op,pr}} :=
\FactProp^{\aug}_{\langle\chirAss\rangle}(X)$. The proof is in four steps: (1) construct the
adjunction in $\cV$; (2) upgrade to an equivalence on the
conilpotent-complete locus; (3) lift along Hackney--Robertson; and
(4) verify \ref{A2-ii}, \ref{A2-iii}.

\emph{Step 1: Adjunction in $\cV$.}
Consider the chiral tensor coalgebra
$\Tc_{\cV}(s^{-1} \bar \cA) := \bigoplus_{n\geq 0} (s^{-1}\bar\cA)^{\otimes_\star n}$
of the desuspended augmentation ideal of a factorization algebra
$\cA \in \Fact^{\aug}(X)$, taken in the $\star$-monoidal ambient of
Proposition~\ref{prop:fg-ambient-properties} (not the $\otimes^{\ch}$
pseudo-tensor). It carries the deconcatenation coproduct and an
alternating-sign differential given by the factorization composition
along collisions on $\Ran(X)$. This is $\Bbarch_X(\cA)$.

Dually, for an augmented conilpotent-complete factorization coalgebra
$\cC$, the cofree tensor algebra
$T_{\cV}(s^{-1}\bar\cC)$ with twisted differential $d_\cC + \partial_\tau$
determined by the coradical filtration defines $\Omegach_X(\cC)$.
Adjunction $\Omegach_X \dashv \Bbarch_X$ follows from the universal
property of free and cofree constructions in $\cV$
(\cite[Chapter~IV.5, \S2.4]{GR17} for the $\infty$-categorical
enhancement), combined with the twisting-morphism dictionary
(\cite[Proposition~3.1]{Francis2012}).

\emph{Step 2: Unit and counit equivalences on the conilpotent-complete
locus.}
The algebra-side counit
$\epsilon_\cA\colon \Omegach_X\Bbarch_X(\cA)\to\cA$ is the standard
contraction of the augmented bar-cobar bicomplex. Acyclicity on the
conilpotent-complete locus follows from a spectral-sequence argument:
the bar-length filtration on $\bar B(\cA)$ is exhaustive by
completeness, and each associated graded piece
$\gr^p \bar B(\cA)$ carries the classical Koszul complex for $(\Ass,
\Ass^!)$, which is acyclic over the unit $\{\mathrm{pt}\}$ by
\cite[Theorem~7.4.1]{LV12}. Exactness of the $\star$-monoidal base
change $\Shv^{\DR}(\{\mathrm{pt}\}) \to \Shv^{\DR}(\Ran(X))$ (as a
left-adjoint between stable $\infty$-categories) propagates acyclicity
to the spectral-sequence $E_1$-page; convergence of the
spectral-sequence to the counit morphism is the Mittag-Leffler property
for the bar-length filtration under conilpotent-completeness.

The coalgebra-side unit
$\eta_\cC\colon \cC\to \Bbarch_X\Omegach_X(\cC)$ is the dual
contraction, acyclic by the same argument applied to the cobar-length
filtration on $\Omega(\cC)$, which converges under
conilpotent-completeness on $\cC$ (Milnor's lim$^1$ vanishes for a
pro-nilpotent coradical filtration).

\emph{Step 3: Properad lift via Hackney--Robertson.}
The adjunction constructed in Step~1 is first operadic. Applying the
left adjoint of the Hackney--Robertson inclusion
$\FactOp(X) \hookrightarrow \FactProp(X)$
(Theorem~\ref{thm:hackney-robertson-model}) to each piece produces an
$(\infty,2)$-categorical adjunction on the properadic envelope
generated by the operadic bar--cobar pair, with the bar and cobar
constructions extended graph-wise. Conilpotent-completeness at
properad level means exhaustive radical filtration plus
Mittag--Leffler convergence on every $(n,m)$-valence piece.
Acyclicity of the unit and counit transfers from Step~2 along this
envelope because the extension is computed by colimits over connected
graphs and the radical-filtration spectral sequence is piecewise the
operadic one. This proves the equivalence of~\ref{A2-i} on
$\CoFactProp^{\conil,\comp}_{\langle\chirAss\rangle}(X)$ and
$\FactProp^{\aug}_{\langle\chirAss\rangle}(X)$; arbitrary
factorization properads are outside the assertion.

\emph{Step 4: Restrictions \ref{A2-ii}, \ref{A2-iii}.}
\ref{A2-ii} is pullback along $\{\mathrm{pt}\} \hookrightarrow \Ran(X)$:
the $\star$-tensor on $\Fact(X)$ restricts to the ordinary tensor on
$\Dmod(\{\mathrm{pt}\}) \simeq \Shv^{\DR}(\mathrm{pt})$, and the
factorization unit becomes the ordinary tensor unit. The construction
in Step~1 therefore specialises to
$T^c(s^{-1}\bar \cA)$ with the classical differential, reproducing
\cite[Theorem~11.4.1]{LV12} for $\Ass$. Under the symmetric-monoidal
sub-inclusion $(\Dmod(X),\otimes^!) \hookrightarrow \Fact(X)$, the
point-restriction coincides with the $!$-tensor on $\Dmod(X)$ at a
marked point, yielding the classical statement verbatim.
\ref{A2-iii} is Lemma~\ref{lem:R-twisted-descent} below; we record it
now for reference and prove it in \S\ref{sec:ainf2-R-descent}.
\end{proof}

\begin{remark}[Step~2 Mittag-Leffler: which filtration, which side]
\label{rem:A-inf-2-ml-step-2}
\index{Mittag-Leffler!bar-length vs coradical filtration}
Step~2 of the proof argues convergence of the bar-length spectral sequence
via Mittag-Leffler. The argument is correctly attached as follows.
Conilpotent-completeness on the coalgebra side (hypothesis~(H2) dualised)
ensures $\varprojlim^{1}$ vanishes for the \emph{coradical} filtration on
the codomain coalgebra $\Omegach_X\Bbarch_X(\cA)$, not directly for the
bar-length filtration on $\Bbarch_X(\cA)$. The bridge between the two
filtrations is the augmentation-ideal-completeness hypothesis~(H2) on the
algebra side: under~(H2), the bar-length filtration on $\Bbarch_X(\cA)$ and
the coradical filtration on $\Omegach_X\Bbarch_X(\cA)$ are $\varprojlim$-dual,
and the Mittag-Leffler condition on one transports to the other along the
bar--cobar adjunction. The explicit cofinal tower is
$\{\Bbarch_X(\cA/\bar\cA^{\,n})\}_{n\geq 1}$, which under~(H2) presents
$\Bbarch_X(\cA)$ as a $\varprojlim$, and each finite stage is bar-finite by
construction. Hypothesis~(H3) (finite-dim graded bar pieces) ensures the
stage maps are surjective in every cohomological degree; Mittag-Leffler
follows.

If (H3) fails (the MC4-completion regime, $\Pi 4$ of
\S\ref{sec:ainf2-platonic-obstructions}), surjectivity of stage maps is
the obstruction, realised as a $\varprojlim^{1}$-class in
$H^{\bullet+1}(\Bbarch_X(\cA))$. Vanishing of this class is equivalent to
chain-level convergence; failure of vanishing is the precise chain-level
obstruction to extending Theorem~$A^{\infty,2}$ beyond~(H3).
\end{remark}

\begin{remark}[Fixed curve, relative interior, and Deligne--Mumford boundary]
\label{rem:A-infinity-2-modular-family-scope}
Theorem~\ref{thm:A-infinity-2} is a fixed-smooth-curve theorem. It
does not extend to $\overline{\mathcal{M}}_{g,n}$ by formal base
change. A relative theorem over the interior
$\mathcal{M}_{g,n}$ requires base-change for the relative Ran prestack;
a theorem over the Deligne--Mumford boundary requires, in addition,
nodal factorization sewing.

Let $\pi:\mathcal C\to S$ be a smooth projective family of marked
curves and let $\Ran^{\rel}(\mathcal C/S)\to S$ be the relative Ran
prestack. For $f:S'\to S$, write
$f':\Ran^{\rel}(\mathcal C'/S')\to\Ran^{\rel}(\mathcal C/S)$ for the
induced map. The relative interior obstruction is the base-change
comparison
\[
\alpha_{\mathrm{BC}}:\;
f^{!}\pi^{\Ran}_{*}\Longrightarrow \pi'^{\Ran}_{*}f'^{!}
\]
on relative factorization sheaves. On a representative
$\mathcal F\in\Fact^{\rel}(\mathcal C/S)$ satisfying
(H1)+(H2)+(H3), its failure is measured by
\[
[\alpha_{\mathrm{BC}}]\in
\mathrm{Ext}^{1}_{\Shv^{\DR}(S')}
\bigl(f^{!}\pi^{\Ran}_{*}\mathcal F,\;
\pi'^{\Ran}_{*}f'^{!}\mathcal F\bigr).
\]
Vanishing of this class for the conilpotent-complete subcategory gives
the relative version of Theorem~\ref{thm:A-infinity-2} over
$\mathcal M_{g,n}$. Without that vanishing, the fixed-curve adjunction
does not imply a family-wise adjunction.

Let $D_\Delta\subset\overline{\mathcal M}_{g,n}$ be a boundary divisor
with normalisation $\widetilde C=C'\sqcup C''$ and formal node
$\widehat D_p$. Mok's logarithmic Fulton--MacPherson geometry
\cite[Theorem~3.3.1, Theorem~5.2.3, Corollary~5.3.4]{Mok25} supplies
the normal-crossings and degeneration space on which nodal sewing is
formulated. The chain-level factorization statement is the separate
nearby-cycle comparison
\[
\beta_{\mathrm{nodal}}:\;
\Psi_\Delta(\pi_{\log})_{*}\mathcal F
\Longrightarrow
(\pi_{\log})_{*,D_\Delta}
\bigl(\mathcal F(C')\otimes_{\mathcal F(\widehat D_p)}
\mathcal F(C'')\bigr),
\]
where $\Psi_\Delta$ denotes Beilinson--Drinfeld factorization nearby
cycles. Its obstruction class is
\[
[\beta_{\mathrm{nodal}}]\in
\mathrm{Ext}^{1}_{\Shv^{\DR}(D_\Delta)}
\bigl(\Psi_\Delta(\pi_{\log})_{*}\mathcal F,\;
(\pi_{\log})_{*,D_\Delta}
\bigl(\mathcal F(C')\otimes_{\mathcal F(\widehat D_p)}
\mathcal F(C'')\bigr)\bigr).
\]
Vanishing of $[\beta_{\mathrm{nodal}}]$ at every boundary divisor is
the extra condition for the Deligne--Mumford extension.

The two obstructions are independent. The class
$[\alpha_{\mathrm{BC}}]$ controls horizontal transport over smooth
families; $[\beta_{\mathrm{nodal}}]$ controls sewing at nodal
degenerations. Class~$\mathsf G$ satisfies the nodal condition by
direct free-field sewing. Class~$\mathsf L$ satisfies it under the
generic non-critical Beilinson--Drinfeld chiral sewing hypotheses.
For class~$\mathsf M$, only the weight-completed sewing lane is in
scope; the raw direct-sum class~$\mathsf M$ boundary statement is not
a consequence of Theorem~\ref{thm:A-infinity-2}.

The $R$-twisted descent of Lemma~\ref{lem:R-twisted-descent} is a
fixed-curve configuration-space theorem. Its Fulton--MacPherson
collision extension is hypothesis~\ref{R3} of that lemma; it is still
not a Deligne--Mumford boundary theorem. Downstream uses of
clutching uniqueness or of $\mathrm{obs}_g=\kappa\lambda_g$ over the
compactified base must import the vanishings
$[\alpha_{\mathrm{BC}}]=0$ and $[\beta_{\mathrm{nodal}}]=0$ in the
family under consideration.
\end{remark}

\begin{remark}[Alternative proof lanes: Theorem~A versus Theorem~C]
\label{rem:A-inf-2-ptvv-scope}
\index{Theorem A!alternative proof lanes}
\index{PTVV!belongs to Theorem C, not Theorem A}
Lurie~HA~\S5.5 gives an independent route to the pole-free-point
restriction~\ref{A2-ii}: factorization algebras via little discs and
factorization envelopes reproduce the classical LV12 Koszul pair
without using GR17 or Francis's star-product. The $\PTVV$
shifted-symplectic construction belongs to \emph{Theorem~C}, not
Theorem~A: the PTVV lane
constructs the $(-(3g-3))$-shifted symplectic structure on
$\RMap(\overline{\cM}_g,BG_\cA)$ as a genuinely disjoint path from the
fiber-center Koszul identification, relevant to the characteristic-datum
C0/C1/C2 clauses and to the $\lambda_g$-free formulation of Theorem~D. It
does not provide an alternative proof of the bar--cobar adjunction or
of the reconstruction counit $\Omegach_X\Bbarch_X(\cA)\to\cA$.
Theorem~A is checked by Francis's chiral Deligne theorem,
Lurie~HA~\S5.5, and Hackney--Robertson model-independence; the PTVV
input is reserved for the Theorem~C shifted-symplectic lane.
\end{remark}

\begin{corollary}[Classical Theorem~A from Theorem~$A^{\infty,2}$;
\ClaimStatusConditional]
\label{cor:classical-A-from-A-infinity-2}
\index{Theorem A!descent from A-infinity-2}
The geometric bar--cobar adjunction
\textup{(}Theorem~\textup{\ref{thm:bar-cobar-isomorphism-main}})
and its Verdier-duality intertwining
\textup{(}Theorem~\textup{\ref{thm:bar-cobar-verdier}}) are the
pullback of Theorem~$A^{\infty,2}$ along the cohomological truncation
$\Fact(X) \to \Dmod(X)$ \textup{(}restricting to the $!$-tensor
sub-category\textup{)}.
\end{corollary}

\begin{proof}
Apply Theorem~\ref{thm:A-infinity-2}\ref{A2-ii} and take
cohomological~$H^0$ of the resulting adjoint equivalence. The
conilpotent-complete locus contains all chirally Koszul algebras by
Definition~\ref{def:chiral-koszul-pair} and
Proposition~\ref{prop:conilpotent-koszul}, so the cohomological
equivalence is on the full Koszul locus. Verdier-duality intertwining
follows by applying the $(\infty,2)$-adjoint equivalence to the
biequivariance of $\Bbarch_X$ against Verdier duality on
$\Dmod(\Ran(X))$; the diagonal factorization on $\Ran(X)$ makes
Verdier duality $\star$-self-adjoint, and the functor-level diagram
commutes up to a canonical 2-isomorphism
(\cite[Chapter~IV.5, \S5.2]{GR17}).
\end{proof}

%================================================================
\section{$R$-matrix-twisted $\Sigma_n$-descent}\label{sec:ainf2-R-descent}
%================================================================

The descent lemma relating ordered and symmetric bar for
$\Eone$-chiral algebras is the explicit content of
Corollary~\ref{cor:eight-cor-R-descent} of the unified Koszul
reflection (equivalently, of
Theorem~\ref{thm:A-infinity-2}\ref{A2-iii}).

\begin{proposition}[Classical MC/CYBE output and quantum QYBE input;
\ClaimStatusProvedHere]
\label{prop:classical-cybe-quantum-r-input}
\index{Maurer-Cartan!classical output versus quantum input}
\index{CYBE!classical output}
\index{QYBE!quantum input}
The universal twisting morphism of
Corollary~\ref{cor:eight-cor-twisting-morphism} produces a
classical Maurer--Cartan equation in the ordered convolution algebra,
\[
D\theta_\cA+\tfrac12[\theta_\cA,\theta_\cA]=0.
\]
On the binary collision stratum, if the residue kernel is
$r(z)\in(\End \cA^{\otimes 2})((z))$, the flatness of the classical
logarithmic connection
\[
\nabla_{\mathrm{cl}}
=d-\hbar\sum_{i<j}r_{ij}(z_i-z_j)\,d(z_i-z_j)
\]
is the spectral classical Yang--Baxter identity
\[
[r_{12}(z_{12}),r_{13}(z_{13})]
+[r_{12}(z_{12}),r_{23}(z_{23})]
+[r_{13}(z_{13}),r_{23}(z_{23})]=0
\]
together with the Arnold relation for the logarithmic forms when
$r(z)$ has rational KZ form $\Omega/z$. This is classical output of
the bar differential. A quantum descent datum is extra input: a
formal or meromorphic family
\[
R(z)=1+\hbar r(z)+O(\hbar^2),\qquad
\check R(z):=\tau\circ R(z),
\]
whose checked operators satisfy the braid cocycle and whose ordinary
operators satisfy the quantum Yang--Baxter equation and unitarity of
Lemma~\ref{lem:R-twisted-descent}. QYBE implies CYBE by taking the
$\hbar^2$ coefficient; CYBE and the Maurer--Cartan equation do not
construct $R(z)$ or the local system $L_R$.
\end{proposition}

\begin{proof}
Expanding QYBE for
$R(z)=1+\hbar r(z)+\hbar^2R^{(2)}(z)+O(\hbar^3)$ gives identical
linear terms on both sides. At order~$\hbar^2$, the unknown
$R^{(2)}$ terms cancel, and the remaining difference is precisely
the displayed sum of commutators. Expanding unitarity
$R^{21}(-z)R^{12}(z)=1$ at order~$\hbar$ gives
$r^{21}(-z)+r^{12}(z)=0$. The Maurer--Cartan equation is the same
flatness identity before choosing a quantization; the Arnold relation
annihilates the three logarithmic two-form coefficients on
$\Conf_3(X)$. No step in this expansion produces the higher
coefficients $R^{(m)}(z)$ for $m\geq2$, so quantized descent remains
an additional hypothesis.
\end{proof}

\begin{lemma}[$R$-matrix-twisted $\Sigma_n$-descent, unitary quantum $R$;
\ClaimStatusConditional]
\label{lem:R-twisted-descent-unitary}% renamed 2026-05-17 from lem:R-twisted-descent (collision with ordered_associative_chiral_kd.tex:587)
\index{R-matrix!Sigma-descent}
\index{descent!R-twisted}
Let $\cA$ be an $\Eone$-chiral algebra with a meromorphic unitary
quantum $R$-matrix
$R(z) \in \operatorname{Aut}(\cA \otimes \cA)((z))$; write
$\check R(z):=\tau\circ R(z)$ for the checked braiding. Assume
\begin{enumerate}[label=\textup{(R\arabic*)}]
\item \label{R1} the quantum Yang--Baxter equation
$R_{12}(z_{12})\,R_{13}(z_{13})\,R_{23}(z_{23})
=R_{23}(z_{23})\,R_{13}(z_{13})\,R_{12}(z_{12})$ on
$\{z_1,z_2,z_3\}$-triples; and
\item \label{R2} \emph{unitarity}: $R^{21}(-z)\,R^{12}(z)=\id_{\cA\otimes\cA}$
on the formal punctured disc, where
$R^{21}(w):=\tau\cdot R(w)\cdot\tau$ is the swap-conjugate.
\item \label{R3} \emph{logarithmic collision extension}: the
KZ/Cherednik connection with monodromy $R$ is regular singular along
the Fulton--MacPherson boundary divisors, and its nearby cycles along
each collision divisor identify with the chiral collision product used
in the ordered bar differential of
Convention~\ref{conv:A-infinity-2-ordered-bar-signs}.
\end{enumerate}
Assume also that the meromorphic family is realized as the monodromy
of a flat KZ/Cherednik-type connection on
$\Conf^{\ord}_n(X)$ for each~$n$, with elementary chamber-crossing
operator $\check R_i(z_i-z_{i+1})$ on adjacent factors.
Let $\pi\colon \Ran^{\ord}(X) \to \Ran(X)$ be the ordered-to-symmetric
Ran-torsor \textup{(}stratified principal $\Sigma$-bundle, stratum-wise
principal at each cardinality\textup{)}. Then there exists a
canonical $\Sigma_n$-equivariant local system $L_R$ on the open stratum
$\Conf^{\ord}_n(X)$ whose descent isomorphism for the elementary
transposition $s_i$ is $\check R_i(z_i-z_{i+1})$. Under
\textup{\ref{R3}}, $L_R$ has a nearby-cycle extension to
$\Ran^{\ord}(X)_{=n}$ compatible with the ordered bar differential, and
for every $n\geq 0$:
\[
\barB^{\Sigma}_n(\cA)
\;\simeq\;
\bigl(B^{\ord}_n(\cA)\bigr)^{\Sigma_n\text{-coinv},\; L_R\text{-twisted}}.
\]
Equivalently, $\barB^{\Sigma}_n(\cA)$ is the (homotopy) descent of
$B^{\ord}_n(\cA) \otimes L_R$ along $\pi$.
\end{lemma}

\begin{proof}
\emph{Step 1: Construction of $L_R$.}
The ordered Ran space $\Ran^{\ord}(X)_{=n}$ is stratified by coincidence
type; its top stratum is the open configuration space
$\Conf^{\ord}_n(X) = X^n \setminus \Delta$. Assign to each point
$(z_1,\dots,z_n) \in \Conf^{\ord}_n(X)$ the vector space
$\cA^{\otimes n}$ at that point and to each elementary deck
transformation $s_i$ the isomorphism
\[
\phi_i=\check R_i(z_i-z_{i+1})\colon
s_i^*(\cA^{\otimes n})\longrightarrow \cA^{\otimes n}.
\]
The QYBE of~\ref{R1} is exactly the braid cocycle
\[
\phi_i\,s_i^*(\phi_{i+1})\,(s_i s_{i+1})^*(\phi_i)
=
\phi_{i+1}\,s_{i+1}^*(\phi_i)\,(s_{i+1}s_i)^*(\phi_{i+1})
\]
on triple overlaps; distant generators commute because they act on
disjoint tensor factors. The unitarity condition~\ref{R2} gives
$\phi_i\,s_i^*(\phi_i)=\id$, since $s_i$ sends $z_i-z_{i+1}$ to
$-(z_i-z_{i+1})$ and swaps the two factors. Thus
\ref{R1}+\ref{R2} supply the Coxeter descent cocycle on the ordered
cover. The flat KZ/Cherednik realization supplies the underlying
local system on $\Conf^{\ord}_n(X)$; the cocycle above supplies its
$\Sigma_n$-equivariant descent datum. No quotient of the pure braid
group is used.

Extension to the lower strata of $\Ran^{\ord}(X)_{=n}$ is not a
consequence of \ref{R1}+\ref{R2}. It is exactly hypothesis~\ref{R3}:
nearby cycles along the diagonal strata carry the limit of $L_R$, and
the limiting connection identifies the collision face with the chiral
product appearing in the ordered bar differential. In the pole-free
case $R(z)=1$ and this limit is the ordinary checked swap $\tau$.

\emph{Step 2: Descent at top stratum.}
On the open stratum $\Conf^{\ord}_n(X)$, the map $\pi$ is a principal
$\Sigma_n$-torsor, and descent is the standard equivalence between
sheaves on $\Conf_n(X)$ and sheaves on the ordered cover equipped
with a $\Sigma_n$-cocycle. The ordered bar $B^{\ord}_n(\cA)$ restricted to
$\Conf^{\ord}_n(X)$ is
$\cA^{\boxtimes n} \otimes \Omega^{n-1}_{\Conf^{\ord}_n(X)}(\log D)$,
and its descent to $\Conf_n(X)$ with twist by $L_R$ is by definition
the symmetric bar $\barB^{\Sigma}_n(\cA)$ of
Definition~\ref{def:symmetric-bar} (the bar coefficient in the
symmetric setting is the Arnold 1-form $d\log(z_i - z_j)$, which
transforms under $\Sigma_n$ by the sign character twisted by
the checked operator $\check R(z_i-z_j)$ acting on the fibres).

\emph{Step 3: Extension across the diagonal strata.}
The log Fulton--MacPherson compactification
$\overline{\Conf}_n(X)$ supplies the fixed-curve normal-crossings
boundary on which the nearby-cycle condition is formulated. By
hypothesis~\ref{R3}, nearby cycles of $L_R$ along each collision face
exist and identify the limiting monodromy with the chiral collision
product. The ordered bar differential is a coderivation for
deconcatenation and preserves stratum depth, so descent on a boundary
stratum is the top-stratum descent applied to the nearby-cycle fibre.
For the pole-free case the exceptional-divisor limit is the checked
swap $\tau$, and
the formula reduces to ordinary $\Sigma_n$-coinvariants.

\emph{Step 4: Pole-free specialisation.}
For a chiral algebra with $R(z)=1$ identically, hence
$\check R(z)=\tau$ (the pole-free or
locally-constant case, e.g., Heisenberg; Example~\ref{ex:heisenberg-e1-duality}),
$L_R$ is the trivial local system, and the twisted descent reduces to
ordinary $\Sigma_n$-coinvariants. This reconciles the ordered and
symmetric bar in the locally-constant case.
For nontrivial $R(z)$ (e.g., Yangian; Corollary~\ref{cor:yangian-bar-cobar}),
the two bars differ: $\barB^{\Sigma}_n(\cA)$ carries the monodromy
twist, so its symmetric coalgebra structure is the descended
$L_R$-twisted structure, not the untwisted cocommutative coalgebra on
the ordered tensor coalgebra.
\end{proof}

\begin{remark}[Scope of \textup{\ref{R2}} and \textup{\ref{R3}}]
\label{rem:R-descent-unitarity-scope}
\index{R-matrix!unitarity scope}
\index{descent!scope across families}
Hypothesis~\ref{R2} is satisfied on the finite-dimensional evaluation
module lane of the rational Drinfeld Yangian $Y_\hbar(\fg)$ after the
standard scalar normalization of the rational $R$-matrix, and on the
integrable finite-type lane of trigonometric quantum affine
$U_q(\hat\fg)$ at generic~$q$ after the corresponding normalization.
These are representation-surface statements. They do not assert a
factorization Drinfeld--Kohno equivalence on all of Yangian
category~$\mathcal O$, nor a dg-shifted Yangian / line-operator
comparison. At roots of unity, and for elliptic or dynamical
$R$-matrices of Belavin/Felder type, unitarity and the
regular-singular boundary extension must be checked in the chosen
presentation. For chiral algebras with trivial ordinary
$R$-matrix~$R(z)=1$ (Heisenberg, free fermions, lattice VOAs at
generic rank), the checked braiding is $\check R(z)=\tau$;
unitarity~\ref{R2} is immediate and~\ref{R1} is vacuous.

Hypothesis~\ref{R3} is a separate fixed-curve boundary condition. For
the rational KZ and trigonometric Cherednik connections it is the usual
regular-singular logarithmic extension along the Fulton--MacPherson
boundary on the stated representation lanes; for elliptic and
dynamical $R$-matrices it depends on the chosen compactification and
dynamical-parameter convention. The open configuration-space descent
uses only~\ref{R1}+\ref{R2}. The Ran-level symmetric bar formula
uses~\ref{R3} as well. Beyond these lanes, any descent claim must
prove \ref{R2}+\ref{R3} directly or supply a different symmetric-bar
construction.
\end{remark}

\begin{remark}[Comparison with $\fg^{\Eone}_\cA$ versus $\fg^{\mathrm{mod}}_\cA$]
\label{rem:av-via-descent}
\index{averaging map!via R-twisted descent}
The averaging map
$\mathrm{av}\colon \fg^{\Eone}_\cA \to \fg^{\mathrm{mod}}_\cA$
(\S\ref{sec:e1-first-prose-architecture}) is the dual of the descent
map $\pi^!$ after forgetting the monodromy datum: dualising
$\pi\colon \Ran^{\ord}(X) \to \Ran(X)$ and tensoring with the structure
sheaf gives the $\Sigma_n$-coinvariant projection on the classical
shadow. It does not quantize a classical kernel and it does not, by
itself, produce the full modular characteristic. For affine
Kac--Moody $V_k(\fg)$ in trace-form convention, the classical residue
kernel is
\[
r^{KM}(z)=k\,\Omega/z.
\]
Its trace-form contribution to the scalar diagonal is
$k\,\dim(\fg)/(2h^\vee)$. The full invariant is
\[
\kappa(V_k(\fg))=\dim(\fg)(k+h^\vee)/(2h^\vee),
\]
where the additional $\dim(\fg)/2$ is the Sugawara conformal-vector
shift, not the trace of the descent local system.
\end{remark}

%================================================================
\section{Restrictions and consequences of Theorem~$A^{\infty,2}$}\label{sec:ainf2-downstream}
%================================================================

The following statements are obtained from the unified Koszul reflection
(Theorem~\ref{thm:koszul-reflection}) via its explicit
properadic-envelope form (Theorem~\ref{thm:A-infinity-2}). Each item
names the restriction, pullback, completion, or specialization being
used.

\begin{corollary}[Typed restrictions of $A^{\infty,2}$;
\ClaimStatusConditional]
\label{cor:ainf2-downstream-list}
\index{Theorem A-infinity-2!downstream corollaries}
Under Theorem~\ref{thm:A-infinity-2}, each of the following is a
corollary obtained by restriction, pullback, or specialization:
\begin{enumerate}[label=\textup{(D\arabic*)}]
\item \label{D1} Theorem~A (classical, ordered--bar statement):
\textup{Theorem~\ref{thm:bar-cobar-isomorphism-main}}. Descent:
Corollary~\ref{cor:classical-A-from-A-infinity-2}.
\item \label{D2} Bar--cobar adjunction:
\textup{Theorem~\ref{thm:bar-cobar-adjunction}}. Descent: first
sentence of Theorem~\ref{thm:A-infinity-2} specialized to chain level
via cohomological truncation.
\item \label{D3} Geometric counit:
\textup{Theorem~\textup{\ref{thm:geom-unit}}}. Descent:
\ref{A2-ii} of Theorem~\ref{thm:A-infinity-2} applied to the counit of
the adjunction, which is $\Omegach_X\Bbarch_X \to \id$ and at a
point is the classical bar-cobar counit on~$\cA$.
\item \label{D4} Bar--cobar--Verdier intertwining:
\textup{Theorem~\textup{\ref{thm:bar-cobar-verdier}}}. Descent:
Verdier-biequivariance of $\Bbarch_X$ at $(\infty,2)$-level, which
restricts to the ordinary chain level
(Corollary~\ref{cor:classical-A-from-A-infinity-2}).
\item \label{D5} Cobar-on-free identity:
\textup{Theorem~\textup{\ref{thm:cobar-free}}}. Descent: $\Omegach_X$
preserves the cofree coalgebra structure by adjunction; pullback to
the pole-free point recovers the classical cobar-of-cofree identity.
\item \label{D6} Fundamental theorem of twisting morphisms:
\textup{Theorem~\textup{\ref{thm:fundamental-twisting-morphisms}}}.
Descent: the $(\infty,2)$-adjoint equivalence is equivalent to the
statement that twisting morphisms $\tau\colon \cC \to \cA$ between a
conilpotent-complete coalgebra and a complete algebra are in natural
bijection with both $\Bbarch_X$-morphisms and $\Omegach_X$-morphisms
(the $(\infty,2)$-Yoneda lemma).
\item \label{D7} Koszul pair characterisation via seven-fold hub-and-spoke TFAE:
\textup{Theorem~\textup{\ref{thm:ftm-seven-fold-tfae-via-hub-spoke}}}
(Vol~I \texttt{ftm\_seven\_fold\_tfae\_platonic.tex}).
Descent: the six bidirections from each spoke to the PBW $E_2$-collapse
hub are immediate from the $(\infty,2)$-adjoint equivalence
restricted to classes of objects. The seventh spoke
(SC-formality) is a class~$\mathsf{G}$ equivalence via
\textup{\textup{\ref{A2-iii}}} and the shadow tower truncation at depth~$2$;
the unitarity hypothesis~\ref{R2} of~\ref{A2-iii} is vacuous on
class~$\mathsf{G}$ where $R(z)=1$ and $\check R(z)=\tau$
(Heisenberg, free fermions,
lattice VOAs at generic rank), so the descent applies unconditionally
on the class-$\mathsf{G}$ stratum.
Spoke~5 (bar concentration in weight~1) extends to $g\geq 1$
only for class~$\mathsf{G}$.
\item \label{D8} Vol~II bridge-table entry for chiral bar--cobar
in the factorization ambient: \textup{Vol~II, \S Bridge~I.3.2}.
Descent: direct restatement of the $(\infty,2)$-equivalence for
3d HT factorization observables.
\item \label{D9} Vol~III CY-to-chiral two-stage factorisation
$\Phi_d = \SpCh_{\Sigma_{d-1}, C} \circ \PhiFA_d$ as an
$(\infty,2)$-functor: \textup{Vol~III, \S CY-A;
\textit{cy\_to\_chiral.tex} Theorem~phi-two-stage-factorisation}.
Descent: stage~$1$ $\PhiFA_d\colon \mathrm{CY}_d\text{-}\mathsf{Cat}
\to E_d\text{-}\mathrm{HolFA}(\CY_d)$ is a canonical
$E_d$-holomorphic factorisation algebra on the CY$_d$ variety
(pinned by Kontsevich--Tamarkin $E_d$-formality and
Costello--Gwilliam--Li locality); stage~$2$
$\SpCh_{\Sigma_{d-1}, C}$ is factorisation homology along a closed
$(d-1)$-cycle followed by restriction to the reference curve
$C \subset \CY_d$, factoring through $\Fact(C)$ at the
$(\infty,2)$-categorical level. Theorem~$A^{\infty,2}$ provides
the bar-cobar equivalence that realizes the CY-A$_3$
$(\infty,2)$-categorical statement on each member of the family of
chiral shadows indexed
by $(\Sigma_{d-1}, C)$.
\item \label{D10} Deligne--Tamarkin formality at chain level:
\textup{Proposition~\textup{\ref{prop:deligne-tamarkin-chain}}}.
Descent: the bar coalgebra $\bar B(\cA)$ in $\Fact(X)$ is formal as a
factorization coalgebra iff $\cA$ is Koszul (a specialization of
Theorem~\ref{thm:A-infinity-2} to the formal locus).
\item \label{D11} Chiral HKR identification:
\textup{Proposition~\textup{\ref{prop:chiral-HKR}}}. Descent:
$\ChirHoch^\bullet(\cA) = \RHom_{\cA \otimes \cA^{op}}(\cA,\cA)$ is
computable via $\bar B(\cA)$ as a resolution; Theorem~$A^{\infty,2}$
gives the bar-cobar tool, HKR is the resulting chain-level
identification.
\item \label{D12} Quillen equivalence
$\mathrm{Ho}(\mathrm{dg\text{-}Ch\text{-}alg}) \simeq
\mathrm{Ho}(\mathrm{conil\text{-}dg\text{-}}\cC^{!}_{\ch}\text{-coalg})$:
\textup{Theorem~\textup{\ref{thm:quillen-equivalence-chiral}}}. Descent:
homotopy-categorical truncation of Theorem~$A^{\infty,2}$; this is the
chain-level theorem whose Vallette-ambient proof is mis-scoped. The
correct proof is via
Theorem~\ref{thm:A-infinity-2} restricted to chain level.
\item \label{D13} $d^2=0$ on the fixed-curve Ran tower:
\textup{Theorem~\textup{\ref{thm:d-squared-zero-universal}}}. Descent:
the cobar differential on $\barB(\cA)$ squares to zero because it is
the image of the simplicial differential on the Ran tower under
$\Omegach_X$; the $(\infty,2)$-equivalence makes this identification
canonical on a fixed smooth curve. The relative-family version over
$\overline{\mathcal M}_{g,n}$ additionally requires the vanishings
$[\alpha_{\mathrm{BC}}]=0$ and $[\beta_{\mathrm{nodal}}]=0$ of
Remark~\ref{rem:A-infinity-2-modular-family-scope}.
\item \label{D14} Fixed-curve ordered Theta-MC recursion:
\textup{Theorem~\textup{\ref{thm:recursive-existence}}}. Descent:
the universal twisting morphism attached to the counit
$\Omegach_X\Bbarch_X(\cA)\to\cA$ gives the fixed-curve ordered
Maurer--Cartan recursion
$D\theta_\cA+\tfrac12[\theta_\cA,\theta_\cA]=0$ at each
$\bar B^{\ord}_n$ level. The quantized QYBE datum, the relative-family
extension over $\overline{\mathcal M}_{g,n}$, and any full cyclic
deformation theorem require the additional hypotheses recorded in
Proposition~\ref{prop:classical-cybe-quantum-r-input} and
Remark~\ref{rem:A-infinity-2-modular-family-scope}.
\end{enumerate}
\end{corollary}

\begin{proof}
Each descent is either (a) pullback along
$\{\mathrm{pt}\} \hookrightarrow \Ran(X)$, (b) cohomological
truncation from $(\infty,2)$- to chain-level, or (c) restriction to a
named sub-$(\infty,2)$-category (e.g., $\Eone$-chiral via
$\Ran^{\ord}$ replacing $\Ran$). The labelling above
specifies which move applies in each case; each move is
functorial at the $(\infty,2)$-level by
Proposition~\ref{prop:fg-ambient-properties} and
Theorem~\ref{thm:hackney-robertson-model}.
\end{proof}

\begin{remark}[Cross-volume bridges to climax and conductor chapters]
\label{rem:cross-volume-bridges-to-climax-and-conductor}
\index{cross-volume bridge!climax and conductor}
The unified Koszul reflection
(Theorem~\ref{thm:koszul-reflection}) feeds directly into two
parallel-established chapters:
\begin{itemize}
\item \textbf{Climax chapter} \textup{(}\ref{chap:climax-platonic})
identifying $\bar\partial=\KZ^{*}(\nabla_{\Arnold})$ as the bar
differential on the universal Arnold connection: the unit~$\eta$ of
the Koszul reflection at the geometric Arnold connection produces the
Knizhnik--Zamolodchikov pullback identification of the bar
differential.
\item \textbf{Universal conductor chapter}
\textup{(}\ref{chap:universal-conductor}) proving
$K=-c_{\mathrm{ghost}}(\mathrm{BRST})$ as the universal ghost-charge
conductor: the conductor
$K^{\kappa}(\cA)=\kappa(\cA)+\kappa(\cA^{!})$ is the numerical
observable of the Verdier-dualized Koszul pair. It is not the
bar-cobar reconstruction functor and it does not assert
$K_X^2\simeq\mathrm{id}$.
\end{itemize}
\end{remark}

%================================================================
\section{Symmetric monoidal ambient corrections}\label{sec:ainf2-heals}
%================================================================

Theorem~$A^{\infty,2}$ uses the following ambient replacements.

\begin{remark}[Symmetric-bar and ordered-bar forms]
\label{rem:ainf2-heal-69}

The proof of
Theorem~\ref{thm:e1-chiral-koszul-duality} invokes
\cite[Theorem~11.4.1]{LV12} in the ambient $(\Dmod(X),\otimes^{\ch})$,
which is a chiral pseudo-tensor structure without genuine bifunctor
or unit. The factorization form has two parts:
\begin{itemize}
\item[\textsc{Symmetric}:] The \emph{symmetric-bar} statement lies
in $\Fact(X)$ under $\star$
(Proposition~\ref{prop:fg-ambient-properties}), where the symmetric
monoidal structure is a genuine bifunctor with a strict unit. The
LV12 transfer is then valid at chain level, and the
$(\infty,2)$-enhancement is Theorem~\ref{thm:A-infinity-2}.
\item[\textsc{Ordered}:] The \emph{ordered-bar} statement is
\ref{A2-iii} of Theorem~\ref{thm:A-infinity-2}: the
ordered bar is the lift to $\Ran^{\ord}$ with $R$-twisted local system
$L_R$, and descent to $\Ran$ recovers the symmetric form up to the canonical
twist.
\end{itemize}
Both forms are proven on their stated hypotheses. The
primitive object is $B^{\ord}(\cA)$ on $\Ran^{\ord}(X)$; the symmetric
bar is the $L_R$-twisted $\Sigma_n$-coinvariant descent image.
\end{remark}

\begin{remark}[Correct unit functor]
\label{rem:ainf2-heal-70}

The operadic Koszul transfer uses a symmetric monoidal functor
$k\text{-}\mathrm{Mod} \to \Dmod(X)$,
$M \mapsto M \otimes \mathbf{1}_{\mathcal{V}}$. There is no
strict unit object in $(\Dmod(X), \otimes^{\ch})$; the chiral unit is
a factorization structure, not a tensor unit.
The correct ambient for this step is
$\Fact(X)$ under $\star$, where the factorization unit
(the constant factorization algebra on $\cO_X$) is the genuine unit.
The symmetric monoidal inclusion
$\Shv(\mathrm{pt}) \hookrightarrow \Fact(X)$, $M \mapsto M \otimes \mathbf{1}_{\Fact(X)}$,
is the correct unit functor
(\cite[Chapter~IV.5, \S2.2]{GR17}). The operadic transfer argument
therefore applies in $\Fact(X)$, not in the chiral pseudo-tensor
ambient.
\end{remark}

\begin{remark}[$R$-twisted descent]
\label{rem:ainf2-heal-71}

The Heisenberg bar is already $\Sigma$-coinvariant. This is compatible
with the ordered $E_1$ formulation because Heisenberg has
$R(z)=1$ and checked braiding $\check R(z)=\tau$,
so by Lemma~\ref{lem:R-twisted-descent} Step~4 the $L_R$-twisted
descent degenerates to ordinary $\Sigma_n$-coinvariants. Hence
Heisenberg's ordered and symmetric bar coincide as a \emph{special case}
of the general $R$-twisted descent.
\end{remark}

\begin{remark}[Francis--Gaitsgory model structure
replaces Vallette]
\label{rem:ainf2-heal-72}

The chiral Quillen-equivalence statement cites
\cite[Theorem~2.1]{Val16} `specialised to the chiral operad', but
Val16 assumes the ambient is chain complexes over a field (projective
model structure). Specialisation to a $\Dmod(X)$-enriched cooperad is
not covered by Val16.
The correct reference is the Francis--Gaitsgory--Rozenblyum model
structure on factorization coalgebras
\cite[Chapter~IV.5, Theorem~3.1.2]{GR17} in place of Val16. The
Quillen equivalence \textup{(D12)} of
Corollary~\ref{cor:ainf2-downstream-list} descends from
Theorem~$A^{\infty,2}$ along cohomological truncation to chain level;
this is the correctly scoped statement.
\end{remark}

\begin{remark}[Cousin resolution replaces naive SDR]
\label{rem:ainf2-heal-73}

The HTT SDR contraction lifts a
$k$-Mod splitting to $\Dmod(X)$ verbatim. The category $\Dmod(X)$ has
nontrivial $\Ext^1$ and the direct-sum decomposition fails.
The replacement is a Cousin / Koszul
fibrewise resolution: for a smooth curve $X$, the $\Dmod(X)$
$t$-structure admits a Cousin-type resolution compatible with the
diagonal stratification of $\Ran(X)$, and the SDR holds fibrewise at
each stratum. Alternatively, one restricts to the associated-graded
formality locus (the Koszul locus of
Definition~\ref{def:chiral-koszul-pair}), where the $\Ext^1$ obstruction
vanishes. Theorem~$A^{\infty,2}$ avoids the issue entirely by working at
$(\infty,2)$-level: there is no SDR to lift, and the adjoint
equivalence is constructed directly via the universal property of free
and cofree constructions in $\Fact(X)$.
\end{remark}

\begin{remark}[Truncation-wise Hochschild finiteness]
\label{rem:ainf2-heal-74}

The nilpotent-completion argument hypothesises
$\dim H^\bullet(\cA,\cA) < \infty$, which excludes Virasoro, Yangian,
and critical-level affine KM (all of which have unbounded Hochschild
cohomology).
The usable hypothesis is truncation-wise finiteness with conformal-weight
control: for any chiral algebra with positive-energy conformal
weight grading
$\cA = \bigoplus_{n\geq 0} \cA_n$ and finite-dimensional
weight spaces $\cA_n$, the bar complex $\bar B(\cA)$ is
truncation-wise finite (each conformal weight stratum
$\bar B(\cA)_{\leq N}$ has finite-dimensional cohomology), and
Theorem~$A^{\infty,2}$ applies to the pro-nilpotent completion
$\hat\cA := \varprojlim_N \cA / \cA_{\geq N}$. This weakening captures
Virasoro (weight space $\cA_n = S^n \Vir_0 / \mathrm{null}$ with
finite dimension), Yangian (weight grading by spectral-parameter
order), and critical KM (weight grading by conformal weight of
the current algebra). The resulting equivalence is the weight-completed
$(\infty,2)$-adjoint equivalence, which is the
correct scope for these motivating targets. Direct-sum-strict
equivalence would over-reach: the relevant ambient category is the
pro-nilpotent or weight-completed one, not the naive direct-sum
ambient.
\end{remark}

\begin{remark}[Correct cross-volume citation]
\label{rem:ainf2-heal-195}

Vol~II cites
`[Theorem~A]{Vol~I}' as the authority for bar--cobar. The Vol~I
Theorem~A is the ordered bar coassociative coalgebra statement with a
fixed-curve factorization form and an $R$-twisted ordered form.
The precise cross-volume reference is:
Theorem~$A^{\infty,2}$ (this chapter,
Theorem~\ref{thm:A-infinity-2}) for the factorization-properad
$(\infty,2)$-adjoint equivalence, and Theorem~A
(Theorem~\ref{thm:bar-cobar-isomorphism-main}) for the chain-level
specialization at a marked point.
\end{remark}

%================================================================
\section{Formal smoothness of chirally Koszul algebras}\label{sec:ainf2-formal-smoothness}
%================================================================

\begin{corollary}[Chiral Koszulness implies properadic-envelope formal
smoothness; \ClaimStatusConditional]
\label{cor:chiral-KK-formal-smoothness}
\index{formal smoothness!chiral Koszul implies}
\index{Koszul Kontsevich!formal smoothness}
Let $\cA$ be a chirally Koszul factorization algebra on $X$
\textup{(}Definition~\textup{\ref{def:chiral-koszul-pair}}).
Then $\cA$ is formally smooth in the properadic envelope
$\FactProp^{\aug}_{\langle\chirAss\rangle}(X)$: for every nilpotent
extension $R \to R_0$ of dg algebras with $\ker$ square-zero and
every $R_0$-valued point
$\Spec R_0 \to \Fact^{\aug}(X)$ factoring through $\cA$, there exists
an $R$-valued lift
$\Spec R \to \FactProp^{\aug}_{\langle\chirAss\rangle}(X)$ extending
the $R_0$-valued point, unique up to contractible space of choices.
\end{corollary}

\begin{proof}
Formal smoothness of a factorization algebra is equivalent, by the
$(\infty,2)$-adjoint equivalence of Theorem~\ref{thm:A-infinity-2}, to
acyclicity of the cotangent complex of its bar coalgebra in
$\CoFactProp^{\conil,\comp}_{\langle\chirAss\rangle}(X)$. For a
Koszul algebra, the bar
coalgebra is cofree (the generators are the desuspended augmentation
ideal, and the differential is determined by the $\theta$-MC
structure); cofree coalgebras have acyclic cotangent complexes
(\cite[Proposition~11.2.4]{LV12}, transferred to $\Fact(X)$ via
Proposition~\ref{prop:fg-ambient-properties}). The extension to
properadic-envelope level uses Theorem~\ref{thm:A-infinity-2}\ref{A2-i} and
Hackney--Robertson: cofree coproperads over conilpotent-complete
coproperads have acyclic cotangent complexes, with proof analogous
to the operadic case, because the graph-wise structure of the
cotangent complex decomposes along connected components of each
graph at each $(n,m)$-valence level.
Hence $\cA$ lifts along any square-zero extension, which is the
definition of formal smoothness in the properadic envelope.
\end{proof}

\begin{remark}[Compatibility with the five-theorem architecture]
\label{rem:ainf2-architecture}
The unified Theorem~A
(Theorem~\ref{thm:koszul-reflection}) is the bar--cobar spine of the
volume. It occupies the first place in the five-package architecture
$A,B,C,D,H$: Theorems~B and~D use its ambient-qualified inversion and
obstruction theory, Theorem~C uses its Koszul-dual Verdier surface,
and Theorem~H uses its chiral Hochschild control on the Koszul/generic
locus. The reconstruction and classification surfaces denoted by
$F$ and $G$ are downstream consequences of this spine rather than
additional main theorem packages. The 14 downstream corollaries of
Corollary~\ref{cor:ainf2-downstream-list} record these consequences
without changing the five-package theorem count.
\end{remark}

%================================================================
\section{Platonic obstructions: four named conjectures}\label{sec:ainf2-platonic-obstructions}
%================================================================

The fully universal Koszul reflection on all of
$\Alg^{\fact,\aug}_X$ without~(H3) is governed by four named open
conjectures.

\begin{conjecture}[$\Pi 1$: Francis--Gaitsgory transfer]
\label{conj:fg-transfer}
The $(\infty,1)$-categorical bar--cobar Quillen equivalence transfers
from $\IndCoh(\Ran(X))$ to $\Alg^{\fact,\aug,\comp}_X$ and its
coalgebra dual without modification.
\end{conjecture}
Francis and Lurie supply the expected transfer theorem
\textup{(}Francis~HA appendix; Lurie HA~\S5.5\textup{)}. This
manuscript still needs a named transfer proposition
\texttt{prop:chiral-quillen-transfer} before the conjecture can be
used as a theorem.

\begin{conjecture}[$\Pi 2$: $E_n$-bar--cobar at higher chiral
dimension]
\label{conj:en-bar-cobar-higher-d}
For $d\geq 2$, the $E_n$-bar functor on $n$-dimensional factorization
$E_n$-algebras admits a left adjoint (cobar) that is a Quillen
equivalence onto conilpotent CDG-coalgebras over the appropriate
$n$-dimensional Maurer--Cartan complex. The $n=1$ case is
Theorem~\ref{thm:koszul-reflection}.
\end{conjecture}
This is the load-bearing direction connecting Vol~I to Vol~III's
CY-to-chiral functor. Currently open in the chiral setting (proved in
Lurie~HA~\S5.5.3 for the topological setting).

\begin{conjecture}[$\Pi 3$: Lagrangian--Koszul converse]
\label{conj:lagrangian-koszul-converse}
Lagrangian transversality of $M_{\mathrm{comp}}$ at $[\cA]$ implies
chiral Koszulness of $\cA$.
\end{conjecture}
This requires the chiral PTVV shifted-symplectic construction.

\begin{conjecture}[$\Pi 4$: Unbounded-rank Koszul reflection]
\label{conj:unbounded-rank-koszul-reflection}
On the locus of complete augmented chiral algebras with
non-finite-dim graded bar pieces (failing hypothesis~(H3)), the
Koszul reflection of Theorem~\ref{thm:koszul-reflection} still
holds in the coderived category but not at the chain level. The
chain-level upgrade requires a yet-unidentified Mittag-Leffler-type
condition on the bar filtration.
\end{conjecture}
The hypothesis~(H3) is satisfied throughout the standard landscape
(Heisenberg, Kac--Moody, Virasoro, $W_N$), so this obstruction is
inactive for the named standard-landscape applications. It marks the precise frontier
between the Koszul reflection on
$\Kosz^{+}(X)$ and the fully universal Koszul reflection on all of
$\Alg^{\fact,\aug}_X$.

%================================================================
\section{Comparison with independent constructions}\label{sec:ainf2-hziv}
%================================================================

\begin{remark}[Independent constructions for Theorem~$A^{\infty,2}$]
\label{rem:ainf2-hziv}
\index{Theorem A-infinity-2!comparison constructions}
The proof of Theorem~\ref{thm:A-infinity-2} uses the following
machinery:
\begin{itemize}
\item Francis 2012 factorization $\star$-product and its universal
adjunctions, \cite{Francis2012};
\item Gaitsgory--Rozenblyum factorization $\infty$-category and model
structure, \cite[Chapter~IV.5]{GR17};
\item Hackney--Robertson $\infty$-properad model structure,
\cite{HackneyRobertson2019};
\item Loday--Vallette classical Koszul bar--cobar at chain level,
\cite[Theorem~11.4.1]{LV12} (used only at pole-free restriction);
\item Mok25 logarithmic Fulton--MacPherson nearby-cycle compatibility
(used only for the descent lemma's extension across diagonal strata).
\end{itemize}

The same theorem is checked against three constructions whose
load-bearing inputs are different:
\begin{itemize}
\item \textbf{(a) Francis 2012 chiral Deligne conjecture} \cite{Francis2012}
for factorization algebras: the chiral Deligne conjecture provides a
$(\infty,2)$-level chiral brace structure on the Hochschild cohomology
of a factorization algebra, whose existence is equivalent to (and
independently derivable from) the chiral bar--cobar equivalence at
the properadic-envelope level. This route uses vanishing of the brace
obstruction class at conilpotent completeness instead of the
$\star$-product adjunction.
\item \textbf{(b) Lurie HA Chapter~5.5 factorization algebras}
\cite[\S5.5]{HA}: independent $(\infty,1)$-categorical construction
of factorization algebras via the little-discs operad and
factorization envelopes. This provides a $(\infty,1)$-level bar--cobar
pair which pulls back to the classical LV12 at chain level, giving an
independent check of the pole-free restriction
\ref{A2-ii} of Theorem~\ref{thm:A-infinity-2} that does not invoke
GR17 or Francis 2012's $\star$-product.
\item \textbf{(c) Hackney--Robertson properad infinity-category}
\cite{HackneyRobertson2019} model-independent of factorization: the
$\infty$-properad construction is independent of the factorization
ambient. It supplies the model structure used in the properadic
envelope of \ref{A2-i}; the transfer is restricted to the
conilpotent-complete envelope generated by the operadic bar--cobar
pair.
\end{itemize}
\end{remark}

\begin{remark}[Independent constructions for bar-cobar reconstruction]
\label{rem:ainf2-hziv-koszul-reflection}
\index{bar-cobar reconstruction!comparison constructions}
The unified bar-cobar reconstruction theorem
Theorem~\ref{thm:koszul-reflection} uses the four absorbed
corollaries: twisting morphism, counit quasi-isomorphism, coalgebra-side
unit weak equivalence, and properad equivalence. The same reconstruction
is tested against the three constructions listed in
Remark~\ref{rem:ainf2-hziv}, each of which provides a
bar-cobar reconstruction check that does not route through the
$\star$-product adjunction alone. Specifically:
\begin{itemize}
\item Francis~2012 chiral Deligne conjecture provides a brace-level
check of the reconstruction counit via the brace algebra structure on
the derived endomorphisms.
\item Lurie HA~\S5.5 little-discs construction provides a topological
check of the $E_1$-input bar-cobar comparison via
the factorization envelope of the $E_1$ algebra.
\item Hackney--Robertson model-independent properad construction provides
a transfer-level check that the reconstruction comparison persists across the
operad-to-properad lift.
\end{itemize}
\end{remark}

%================================================================
\section*{Theorem~A as the algebraic structure on the KZ functor}
%================================================================

One adjunction, one reconstruction counit, one Verdier-dualized
duality functor. Theorem~$A^{\infty,2}$ acts by restriction,
cohomological truncation, and conilpotent completion; it does not
identify reconstruction with Koszul duality, does not turn classical
CYBE data into a quantum $R$-matrix, and does not extend a fixed-curve
statement over the Deligne--Mumford boundary without the two
base-change and nodal-sewing vanishings. Theorem~A enters the
five-theorem spine of Volume~I as the algebraic structure on the KZ
functor of Chapter~\ref{chap:climax-platonic}: the pullback identity
$\bar\partial = \KZ^{*}(\nabla_{\Arnold})$ is the bar differential read
through the Koszul reflection.

\section{K3 Hall--Drinfeld input and Theorem~A scope}
\label{sec:tainf2-supplement}

\begin{remark}[$A_\infty$-structure on $\mathbf H_{\Delta_5}$ as external input]
\label{rem:tainf2-1}
Theorem~A supplies the completed bar--cobar ambient for a fixed chiral
shadow of a supplied factorization algebra. It does not construct the
K3 Hall--Drinfeld object $\mathbf H_{\Delta_5}$, does not identify it
with a Drinfeld Yangian, and does not compute its higher products. If
Vol.~II/III supply a completed K3 chiral shadow
$\mathbf H_{\Delta_5}$ with $A_\infty$ structure maps
\[
\mu_n: \mathbf H_{\Delta_5}^{\otimes n}\to \mathbf H_{\Delta_5},\qquad n\ge 2,
\]
then this chapter applies only after hypotheses \textup{(H1)}--\textup{(H3)}
and the relevant $R$-descent hypotheses have been verified on that
shadow. The proposed first products
\[
\mu_2=\text{Hall multiplication in }\mathrm{CoHA}_{K3\times E},\qquad
\mu_3=\text{Drinfeld-associator coboundary at order }\hbar,
\]
and
\[
\mu_4=\text{Igusa-form twist at order }\hbar^2
\quad\text{from}\quad \Phi_{10}/\eta^{24}
\]
belong to the K3/Hall--Drinfeld input surface. The order
$\hbar^{\leq3}$ pentagon coboundary
\[
\phi^{(3)} = \zeta(3)c_{\mathrm{symm}}
+ \tfrac{25}{3}c_{\mathrm{timelike}}
+ (\Phi_{10}/\eta^{24})c_{\Phi_{10}}
\]
is likewise external structure data. Theorem~A can transport such data
through the completed bar--cobar adjunction after they are supplied; it
does not prove the K3 product formulas.
\end{remark}
