\chapter{Three Hochschild comparison surfaces: curve cochains, mode
shadows, and critical centres}
\label{chap:three-hochschild-unification}

\index{Hochschild cohomology!comparison surfaces|textbf}
\index{chain map!ChirHoch to HH mode}
\index{chain map!HH mode to GF}
\index{Gel'fand--Fuchs cohomology}
\index{Feigin--Frenkel centre!degree-zero comparison}

Three constructions carrying Hochschild language meet a chiral algebra,
but only one is Theorem~H. The local chiral Hochschild cochain complex
on the reference curve is the tangent complex of the chiral MC moduli. The
associative Hochschild complex of a chosen formal-disk mode algebra is
a fibrewise algebraic shadow. The Gel'fand--Fuchs complex is continuous
Lie algebra cohomology of the positive modes; it is not Hochschild
cohomology, and scalar GF cochains appear only after a coefficient
choice.

The comparison maps live only on this formal-disk surface and only to
their images. They do not identify local chiral Hochschild cochains with
the categorical Hochschild cochains of a dg or Calabi--Yau category, with
topological Hochschild homology of a ring spectrum, or with the
product-ambient/Hall Hochschild theories of Vol.~III. Those theories
have different inputs, coefficient objects, and ambient products.
Theorem~H remains the curve-level statement for
$\ChirHoch^\bullet$ on a fixed reference curve; Theorem~C remains the
scalar centre-complementarity statement at the scope recorded in
Theorem~\ref{thm:derived-centre-complementarity-strengthened}.
At critical level the Feigin--Frenkel centre compares the chiral and
mode centres in degree zero; ordinary trivial-coefficient GF
cohomology is not thereby identified with the oper algebra.

\section{Three complexes, three gradings, three operads}
\label{sec:three-three-three}

Fix a chiral algebra~$\cA$ on a smooth projective reference curve~$X$
with vacuum section $\mathbf{1}\in\cA$ and $\cD_X$-module structure.
Choose a formal coordinate at a point of~$X$ and a PBW-filtered
formal-disk mode algebra $A_{\mathrm{mode}}$ associated with that
choice. The non-critical statements assume that $\cA$ lies on the
proved Theorem~H surface: PBW chiral Koszul, $E_\infty$-completed,
finite-type/perfect, and away from critical affine levels and the
non-generic simple-quotient points excluded in
Theorem~\ref{thm:main-koszul-hoch}. Critical-level statements are
confined to~\S\ref{sec:critical-level-ff}. Whenever a scalar
Gel'fand--Fuchs target is used, a continuous invariant functional or a
central-extension coefficient module is part of the data.

\begin{definition}[The three comparison complexes; \ClaimStatusProvedElsewhere]
\label{def:three-hochschild-complexes}
The three complexes are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Chiral Hochschild cochains} $\ChirHoch^*(\cA)$: the
 complex of multilinear
 $\cD_{X^{n+2}}$-module maps
 \[
 \ChirHoch^n(\cA) \;=\;
 \mathrm{RHom}_{\cD_{X^{n+2}}}\!\bigl(j_{n!}j_n^*(\cA^{\boxtimes n+2}),\,
 \Delta_*\cA\bigr)
 \]
 on the configuration space $C_{n+2}(X)$, with differential induced
 by collision residues along divisors $D_{ij}=\{z_i=z_j\}$, as in
 Chapter~\ref{chap:deformation-theory}. Spectral data: the formal
 variables $\lambda_1,\ldots,\lambda_{n+1}$ of $\End^{\mathrm{ch}}_\cA$
 attached to relative positions.
\item \emph{Mode-algebra Hochschild cochains}
 $\HH^*(A_{\mathrm{mode}},A_{\mathrm{mode}})$: the classical Hochschild
 complex of the chosen associative formal-disk mode algebra
 $A_{\mathrm{mode}}$. The Zhu algebra and the full mode algebra are
 distinct quotients/completions; a comparison statement must name which
 one is being used. The differential is the standard Hochschild
 differential. The cup product and Gerstenhaber bracket are additional
 structures, not the differential. No curve-level spectral variables
 remain.
\item \emph{Gel'fand--Fuchs continuous cochains}
 $C^*_{\mathrm{cont}}(L_+;M)$: the continuous
 Chevalley--Eilenberg complex of the positive-mode Lie algebra
 $L_+\subset \mathrm{Lie}(A_{\mathrm{mode}})$, computed with respect
 to the topology induced by conformal weight
 \cite{Fuks86,Goncharova73}. The scalar GF complex is the case
 $M=\bC$ with trivial coefficients. Antisymmetrising Hochschild
 cochains naturally gives $A_{\mathrm{mode}}$-valued CE cochains; a
 scalar GF class requires an additional invariant functional or
 coefficient module.
\end{enumerate}
\end{definition}

\begin{remark}[Theorem H on the reference curve]
\label{rem:theorem-H-reference-curve-lane}
The symbol $\ChirHoch^\bullet(\cA)$ denotes the curve-level chiral
Hochschild cochain complex of the chiral algebra~$\cA$ on the fixed
reference curve~$X$. Its cohomology satisfies
\[
 H^n(\ChirHoch^\bullet(\cA))=0 \qquad (n\ge 3)
\]
under the hypotheses of
Theorem~\ref{thm:hochschild-polynomial-growth}, by the ordered
Fulton--MacPherson collision-depth spectral sequence, the
pure-braid Orlik--Solomon contraction, the PBW chiral Koszul
comparison, the averaging step of
Corollary~\ref{cor:hochschild-averaging-symmetric}, and the
curve-level Verdier shift. A nonzero degree-$3$ or higher cohomology
class therefore belongs to another ambient, such as mode-algebra
Hochschild cohomology, continuous GF cohomology, categorical
Hochschild cohomology, or THH, and requires a named comparison
obligation before it can be compared with Theorem~H.
\end{remark}

\begin{remark}[Excluded Hochschild theories]
\label{rem:excluded-hochschild-theories}
\index{Hochschild cohomology!categorical!excluded from Theorem H}
\index{Hall--Drinfeld double!Hochschild scope}
Topological Hochschild homology
$\mathrm{THH}(R)$ is factorization homology of an $E_1$-ring spectrum
over the circle. Its circle action, cyclotomic refinements, and
spectrum-level input are not part of the curve-level
$\ChirHoch^\bullet(\cA)$ complex.

The categorical Hochschild complex
$\HH^\bullet_{\mathrm{cat}}(\mathcal C)$ of a dg category~$\mathcal C$
is the derived endomorphism algebra of the identity functor; with a
compact generator it is Morita equivalent to
$\RHom_{A^e}(A,A)$
(Theorem~\ref{thm:derived-center-hochschild}). For a
Calabi--Yau $d$-category it carries the CY shifted Poisson/BV
structure of the Vol.~III Hochschild calculus. This is not
$\ChirHoch^\bullet(\cA)$ on a curve, and Theorem~H says nothing about
its amplitude.

The product-ambient and Hall Hochschild theories attached to
CoHA/Hall--Drinfeld doubles use product geometry and Hall
convolution. They belong to the Vol.~III ambient. A Stage--2
specialisation functor may produce a chiral algebra on a reference
curve, but the resulting curve-level $\ChirHoch^\bullet$ is a new
chiral object; it is not the categorical or Hall Hochschild complex
itself.
\end{remark}

\begin{remark}[Derived centre and open/closed comparison]
\label{rem:derived-centre-not-physical-bulk-without-comparison}
The chiral derived centre is the cochain-level closed-sector object
\[
 Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)
 := C^\bullet_{\mathrm{ch}}(\cA,\cA)
 = \RHom_{\cA\text{-}\cA}^{\mathrm{fact}}(\cA,\cA),
\]
with its brace dg algebra structure
(Section~\ref{sec:chiral-center-theorem}). It is the endocentral
object through which local closed-sector actions on the boundary
chiral algebra factor. A physical bulk object is not identified with
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ by notation. Such an
identification is a theorem only after a named open/closed comparison
quasi-isomorphism
\[
 \mathrm{OC}_{\cA}\colon
 \mathcal O^{\mathrm{phys}}_{\mathrm{bulk}}(\cA)
 \xrightarrow{\;\sim\;}
 Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)
\]
has been constructed in the relevant open/closed theory. Without
$\mathrm{OC}_{\cA}$, only the cochain-level derived centre is in
scope.
\end{remark}

\begin{remark}[Five-object firewall]
\label{rem:five-object-firewall-three-hochschild}
For a chiral algebra~$\cA$ the five objects
\[
 \cA,\qquad
 B^{\mathrm{ch}}(\cA)=T^c(s^{-1}\bar{\cA}),\qquad
 \cA^{\mathrm i}=H^\bullet B^{\mathrm{ch}}(\cA),\qquad
 \cA^!=(\cA^{\mathrm i})^\vee \text{ after Verdier duality},\qquad
 Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)
\]
are never interchangeable. Bar--cobar inversion is the statement that
$\Omega^{\mathrm{ch}}B^{\mathrm{ch}}(\cA)$ recovers~$\cA$ on the
inversion surface. Verdier Koszul duality produces~$\cA^!$ from the
intrinsic bar-dual coalgebra~$\cA^{\mathrm i}$. The derived centre is
the Hochschild cochain object. None of these constructions produces
one of the other four by a change of name.
\end{remark}

\begin{remark}[Distinguishing gradings]
\label{rem:three-gradings}
The three complexes carry \emph{different} gradings:
\begin{itemize}[nosep]
\item $\ChirHoch^*$ has cochain degree $n$ and an independent
 \emph{spectral filtration} by collision depth
 $p = |\{i<j : z_i = z_j\}|$;
\item $\HH^*(A_{\mathrm{mode}})$ has cochain degree $n$ and a
 conformal-weight grading inherited from $A_{\mathrm{mode}}$;
\item $H^*_{\mathrm{cont}}(L_+;M)$ has antisymmetric
 Lie-cochain degree $n$ and an outer-derivation filtration.
\end{itemize}
Chain-level comparison maps must respect the cochain degree and are
filtered for the secondary gradings. They are not inverse equivalences
of complexes. The maps below land in associated images; the scalar
GF versions require the coefficient datum named above.
\end{remark}

\section{Chain maps: construction}
\label{sec:three-chain-maps}

\begin{construction}[Filtered map $\Theta_1$:
ChirHoch $\to$ HH$_{\mathrm{mode}}$; \ClaimStatusConditional]
\label{constr:theta1-chirhoch-to-HHmode}
\index{Theta 1 intertwiner@$\Theta_1$ intertwiner}
On the Koszul locus at non-critical level, and after the formal
coordinate and PBW-filtered mode model have been fixed, restrict a
chiral Hochschild cochain $\phi\in\ChirHoch^n(\cA)$ to the formal
disk, extract the constant term in the spectral variables
$\lambda_i$, and project to the chosen mode algebra. Explicitly, on
the associated graded of the PBW filtration:
\[
 \Theta_1(\phi)(a_1\otimes\cdots\otimes a_n)
 \;:=\;
 \mathrm{ev}_0\!\bigl[\phi(\widetilde a_1(z_1),\ldots,
 \widetilde a_n(z_n),\mathbf{1}(z_{n+1}))\bigr]\!
 \Bigr|_{\lambda_i=0}
\]
where $\widetilde a_i\in\cA$ is any formal-disk lift of
$a_i\in A_{\mathrm{mode}}$ and $\mathrm{ev}_0$ evaluates at the
colliding configuration $z_1=\cdots=z_{n+1}$. The construction is a
chain map only under the filtered PBW comparison identifying the
formal-disk restriction of the chiral bar differential with the
Hochschild differential of $A_{\mathrm{mode}}$ after quotienting by
the spectral-variable kernel. Without this comparison, it is only a
filtered projection of cochains.
\end{construction}

\begin{construction}[Antisymmetrisation $\Theta_2$:
HH$_{\mathrm{mode}} \to$ CE; \ClaimStatusConditional]
\label{constr:theta2-HHmode-to-GF}
\index{Theta 2 intertwiner@$\Theta_2$ intertwiner}
The associative mode algebra $A_{\mathrm{mode}}$ generates a Lie
algebra $\mathrm{Lie}(A_{\mathrm{mode}})$ via the commutator
bracket. The chosen mode functor sends the positive modes of~$\cA$ to a
closed Lie subalgebra
$L_+\subset \mathrm{Lie}(A_{\mathrm{mode}})$, equipped with the
conformal-weight topology. If the PBW mode model is faithful on
positive modes, this subalgebra identifies with
$\mathrm{Lie}(\cA)_{>0}$; otherwise $L_+$ is the image after quotienting
by the positive-mode kernel. The antisymmetrization
map
\[
 \mathrm{Alt}\colon
 C^n_{\mathrm{Hoch}}(A_{\mathrm{mode}},A_{\mathrm{mode}})
 \;\longrightarrow\;
 C^n_{\mathrm{cont}}(L_+;A_{\mathrm{mode}}^{\mathrm{ad}})
\]
defined by $\mathrm{Alt}(\phi)(x_1\wedge\cdots\wedge x_n)
= \sum_{\sigma\in S_n}\mathrm{sgn}(\sigma)\,
\phi(x_{\sigma(1)},\ldots,x_{\sigma(n)})$ is a chain map of
complexes from Hochschild cochains to Chevalley--Eilenberg cochains
with adjoint coefficients. Given a continuous invariant functional
$\ell\colon A_{\mathrm{mode}}\to M$, or the critical oper coefficient
module in~\S\ref{sec:critical-level-ff}, composition gives a scalar or
$M$-valued map
\[
 \Theta_{2,\ell}:=\ell\circ\mathrm{Alt}\colon
 C^n_{\mathrm{Hoch}}(A_{\mathrm{mode}},A_{\mathrm{mode}})
 \longrightarrow C^n_{\mathrm{cont}}(L_+;M).
\]
There is no canonical map to trivial-coefficient scalar GF cochains
without this coefficient datum. Continuity of the image follows from
the assumption that $\phi$ is polynomial in its mode arguments.
\end{construction}

\begin{construction}[Composite $\Theta_{3,\ell}$:
ChirHoch $\to$ CE/GF image; \ClaimStatusConditional]
\label{constr:theta3-chirhoch-to-GF}
\index{Theta 3 intertwiner@$\Theta_3$ intertwiner}
After choosing the PBW comparison and coefficient datum~$\ell$, define
$\Theta_{3,\ell}:=\Theta_{2,\ell}\circ\Theta_1$. Equivalently,
evaluate a chiral Hochschild cochain on the formal-disk restriction,
restrict further to the positive-mode subalgebra~$L_+$, extract the
constant term in the spectral variables, antisymmetrize, and apply the
coefficient functional. The composition is a chain map precisely under
the hypotheses making both factors chain maps.
\end{construction}

\begin{remark}[No chain map back; asymmetry is structural]
\label{rem:no-chain-map-back}
There is no canonical chain map in the opposite direction. The
positive-mode subalgebra $L_+$ loses the mode $a_{(0)}$ content
encoded in chiral derivations at simple pole order; the Zhu
functor loses the spectral parameters; lifting $\HH^*$ cochains
to $\ChirHoch^*$ requires choosing formal primitives that are
not canonical. The cohomological statements below are image
statements after quotient and coefficient projection, not inverses on
the full truncated complexes.
\end{remark}

\section{Chain-level image comparison in low degrees}
\label{sec:chain-level-agreement-low}

\begin{theorem}[Image-level comparison in low degrees on the Koszul
locus; \ClaimStatusConditional]
\label{thm:three-hochschild-chain-level-agreement-low-degree}
\index{Theorem!three-Hochschild chain-level image comparison}
Let $\cA$ lie on the proved Theorem~H surface named above. Assume the
formal-disk PBW comparison makes $\Theta_1$ a filtered chain map after
quotienting by the spectral-variable kernel, assume the positive-mode
image~$L_+$ and coefficient datum~$\ell$ are fixed for the CE/GF target,
and let $\tau_{\le 2}$ denote stupid truncation to cochain degrees
$\{0,1,2\}$. Then the chosen maps compare the low-degree surfaces only
after passing to the indicated images/quotients:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\Theta_1$ induces a quasi-isomorphism from the quotient of
 $\tau_{\le 2}\ChirHoch^*(\cA)$ by the spectral-variable kernel onto
 its image in $\tau_{\le 2}\HH^*(A_{\mathrm{mode}})$;
\item $\Theta_{2,\ell}\colon
 \tau_{\le 2}\HH^*(A_{\mathrm{mode}}) \to
 \tau_{\le 2} C^*_{\mathrm{cont}}(L_+;M)$ is a chain map whose
 antisymmetric quotient is quasi-isomorphic to its continuous-cochain
 image. When $M=\bC$ with trivial coefficients, this image is only the
 part of scalar GF cohomology detected by~$\ell$;
\item $\Theta_{3,\ell} = \Theta_{2,\ell}\circ\Theta_1$ is therefore a
 chain-level comparison from the chiral quotient to the selected
 continuous-cochain image. It is not asserted to be a quasi-isomorphism
 from the full truncated chiral Hochschild complex, nor onto full
 scalar GF cohomology.
\end{enumerate}
\end{theorem}

\begin{proof}
For~(i), quotienting by the spectral-variable kernel is exactly the
operation that removes the part of the chiral cochain invisible to the
formal-disk mode algebra. The filtered PBW comparison hypothesis then
identifies the induced differential on this quotient with the
Hochschild differential on the image. Hence the quotient maps
quasi-isomorphically onto that image. Theorem~H supplies only the
curve-level cohomological amplitude; it is not used to identify the
mode algebra or to kill the kernel.

For~(ii), antisymmetrisation is the standard Hochschild-to-Chevalley
map from an associative algebra to its commutator Lie algebra with
adjoint coefficients. Composing with~$\ell$ remains a chain map exactly
when~$\ell$ is invariant, or more generally when the chosen coefficient
module makes it a morphism of CE complexes. Thus the statement is an
image statement. It does not assert that every scalar GF class in
degrees~$\le 2$ comes from Hochschild cochains.

For~(iii), composing the quotient comparison in~(i) with the
antisymmetric-image comparison in~(ii) gives the asserted map from the
chiral quotient to the selected continuous-cochain image. The explicit
tables below show why no statement about the full unquotiented
complexes can be true.
\end{proof}

\begin{remark}[Explicit low-degree tables]
\label{rem:three-hochschild-low-degree-tables}
The following low-degree table is a separation witness, not a
surjectivity statement for the comparison maps. It assembles the
individual computations scattered across
Chapter~\ref{chap:deformation-theory} and
Section~\ref{sec:chiral-center-theorem}.
The GF columns use ordinary trivial coefficients; a scalar image of
$\Theta_{2,\ell}$ may be smaller.
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lccc|ccc|ccc}
\toprule
family
& $\ChirHoch^0$ & $\ChirHoch^1$ & $\ChirHoch^2$
& $\HH^0_{\mathrm{mode}}$ & $\HH^1_{\mathrm{mode}}$ & $\HH^2_{\mathrm{mode}}$
& $H^0_{\mathrm{cont}}$ & $H^1_{\mathrm{cont}}$ & $H^2_{\mathrm{cont}}$ \\
\midrule
$\cH_k$, $k\ne 0$
& $\bC$ & $\bC$ & $\bC$
& $\bC$ & $0$ & $0$
& $\bC$ & $0$ & $\bC$ \\
$\cF$ (free fermion)
& $\bC$ & $0$ & $\bC$
& $\bC$ & $0$ & $0$
& $\bC$ & $0$ & $\bC$ \\
$V_k(\fg)$ generic
& $\bC$ & $\fg$ & $\bC$
& $\bC$ & $0$ & $0$
& $\bC$ & $0$ & $\bC\langle\omega_{\fg}\rangle$ \\
$\mathrm{Vir}_c$ generic
& $\bC$ & $0$ & $\bC$
& $\bC$ & $0$ & $0$
& $\bC$ & $0$ & $\bC\langle c_2\rangle$ \\
\bottomrule
\end{tabular}
\end{center}
Here $\omega_{\fg}$ is the standard affine residue/Killing
central-extension cocycle, not the ordinary finite-dimensional
Lie-algebra cohomology group $H^2(\fg;\bC)$.

Define the low-degree alternating characters
\[
 \chi_{\le 2}^{\mathrm{ch}}(\cA)
 :=\sum_{n=0}^{2}(-1)^n\dim H^n(\ChirHoch^\bullet(\cA)),
 \quad
 \chi_{\le 2}^{\mathrm{mode}}(\cA)
 :=\sum_{n=0}^{2}(-1)^n\dim H^n\HH^\bullet(A_{\mathrm{mode}}),
\]
and
\[
 \chi_{\le 2}^{\mathrm{GF}}(L_+)
 :=\sum_{n=0}^{2}(-1)^n
 \dim H^n_{\mathrm{cont}}(L_+;\bC).
\]
For the same four witnesses one obtains:
\[
\begin{array}{c|ccc}
\text{family} & \chi_{\le 2}^{\mathrm{ch}}
& \chi_{\le 2}^{\mathrm{mode}}
& \chi_{\le 2}^{\mathrm{GF}}\\
\hline
\cH_k & 1 & 1 & 2\\
\cF & 2 & 1 & 2\\
V_k(\mathfrak{sl}_2) & -1 & 1 & 2\\
\mathrm{Vir}_c & 2 & 1 & 2
\end{array}
\]
The Heisenberg row is decisive:
$\ChirHoch^\bullet(\cH_k)$ has dimensions $(1,1,1)$ and
$\chi_{\le 2}^{\mathrm{ch}}=1$, whereas the bounded scalar
GF table has dimensions $(1,0,1)$ and
$\chi_{\le 2}^{\mathrm{GF}}=2$. Euler characteristic is therefore
not a comparison invariant for the native complexes.

The table refines
Remark~\ref{rem:critical-level-dimensional-divergence}: the three
theories do \emph{not} have the same cohomological dimensions at
non-critical level. Heisenberg has
$\dim \ChirHoch^1(\cH_k) = 1$ (outer chiral derivation
$D(\alpha) = \mathbf{1}$) while $\dim \HH^1(A_1) = 0$ (all
Weyl-algebra derivations are inner). Affine KM has
$\dim \ChirHoch^1(V_k(\fg)) = \dim(\fg)$ while
$\dim \HH^1(A_{\mathrm{mode}})$ vanishes generically. These outer
chiral derivations lie in the spectral/formal-disk kernel of the mode
projection unless an additional coefficient remembers them. They are
precisely the chiral-specific content missed by
$\HH^*_{\mathrm{mode}}$.
\end{remark}

\begin{remark}[What ``agreement'' means precisely]
\label{rem:three-hochschild-agreement-precision}
Three inequivalent statements are at play:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Identical cohomological dimensions.} FALSE at generic
 level. Witness: $\ChirHoch^1(\cH_k) = \bC$ vs $\HH^1(A_1) = 0$.
\item \emph{Same low-degree Euler characteristic.} FALSE for the
 ordinary scalar GF target. Witness:
 $\chi_{\le 2}^{\mathrm{ch}}(\cH_k)=1-1+1=1$ while
 $\chi_{\le 2}^{\mathrm{GF}}(L_+)=1-0+1=2$. Trivial-coefficient GF,
 adjoint CE, and a scalar anomaly coefficient can give different
 Euler shadows.
\item \emph{Chain-level quasi-isomorphism onto image via
 $\Theta_1,\Theta_{2,\ell},\Theta_{3,\ell}$.} Conditional on the PBW
 and coefficient hypotheses above, and only on the truncated range
 $\tau_{\le 2}$; this is
 Theorem~\ref{thm:three-hochschild-chain-level-agreement-low-degree}.
\end{enumerate}
Statement~(c) is the correct chain-level formulation. Statement~(a)
is false, and statement~(b) is not a theorem without a coefficient
convention.
\end{remark}

\section{Cohomological image comparison on the full range}
\label{sec:three-hochschild-all-degree}

\begin{theorem}[Cohomological image comparison on the full range on the
Koszul locus; \ClaimStatusConditional]
\label{thm:three-hochschild-cohomological-agreement-all-degree}
\index{Theorem!three-Hochschild cohomological image comparison}
Under the hypotheses of
Theorem~\ref{thm:three-hochschild-chain-level-agreement-low-degree},
at non-critical level the induced maps
\[
 [\Theta_1]\colon H^n\ChirHoch^*(\cA)
 \to H^n\HH^*(A_{\mathrm{mode}}),
 \qquad
 [\Theta_{2,\ell}]\colon H^n\HH^*(A_{\mathrm{mode}})
 \to H^n_{\mathrm{cont}}(L_+;M),
\]
are isomorphisms from the corresponding quotient cohomologies onto
their respective images for all $n\ge 0$. The image of
$[\Theta_1]$ in $H^n\HH^*$ is the mode-visible part of the chiral
class. The image of $[\Theta_{2,\ell}]$ in continuous cohomology is
the $\ell$-visible part. No surjectivity onto full scalar GF cohomology
or full mode Hochschild cohomology is asserted, and the native
low-degree Euler characteristics need not agree.
\end{theorem}

\begin{proof}
Cohomological statement: on the Koszul locus Theorem~H gives
$H^n(\ChirHoch^\bullet(\cA)) = 0$ for $n\ge 3$, so
$[\Theta_1]$ is vacuously an isomorphism from the zero source
cohomology onto its image in those degrees. For $n\in\{0,1,2\}$,
Theorem~\ref{thm:three-hochschild-chain-level-agreement-low-degree}
upgrades to a cohomological statement by passage from
chain-level quasi-isomorphism onto image to cohomology. The
antisymmetrization statement is the same argument with coefficients
carried by~$\ell$. Euler characteristic is additive inside a fixed
finite complex or an exact sequence; it is not preserved by a map that
first quotients the chiral complex by the spectral kernel and then
projects to a coefficient-selected CE image. The theorem does not
require, and does not imply, any high-degree vanishing theorem for
$H^*(A_{\mathrm{mode}})$.
\end{proof}

\begin{remark}[Gel'fand--Fuchs unboundedness is a property of
$L_+$, not of $\ChirHoch$]
\label{rem:GF-unbounded-but-image-bounded}
The continuous GF cohomology $H^*_{\mathrm{cont}}(L_+;\bC)$
is a polynomial ring for Virasoro (\cite[Theorem~1.4.3]{Fuks86}:
$H^*(L_+;\bC) = \bC[c_2]$ with $|c_2|=2$;~\cite{Goncharova73}) and
unbounded in general. This unboundedness is a property of the
mode Lie algebra, not of the chiral Hochschild complex. The image of
$\Theta_{3,\ell} = \Theta_{2,\ell}\circ\Theta_1$ is the
$\ell$-visible bounded part: precisely the range where the
antisymmetrization of $\HH^*_{\mathrm{mode}}$ sees continuous-Lie
content after the coefficient choice. Above amplitude $[0,2]$, GF
cohomology may continue while
$H^n(\ChirHoch^\bullet(\cA))=0$. The behaviour of
$H^n\HH^*(A_{\mathrm{mode}})$ is a property of the chosen mode algebra
and is not controlled by Theorem~H.
\end{remark}

\section{Sharp divergence above amplitude \texorpdfstring{$[0,2]$}{[0,2]}}
\label{sec:three-hochschild-divergence}

\begin{proposition}[High-degree divergence from scalar GF;
\ClaimStatusConditional]
\label{prop:three-hochschild-high-degree-divergence}
\index{divergence!three Hochschild at n>=3}
Under the hypotheses of
Theorem~\ref{thm:three-hochschild-chain-level-agreement-low-degree},
the comparison with full scalar GF cohomology cannot extend beyond
the curve-level amplitude:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $H^n(\ChirHoch^\bullet(\cA)) = 0$ for $n\ge 3$ by Theorem~H
 (Theorem~\ref{thm:hochschild-polynomial-growth}).
\item $H^n\HH^*(A_{\mathrm{mode}})$ depends on the chosen
 formal-disk mode algebra; Vol.~I uses no theorem asserting its
 uniform vanishing above degree~$2$.
\item $H^n_{\mathrm{cont}}(L_+;\bC)$ may be nonzero;
 for Virasoro, $H^{2k}_{\mathrm{cont}}(L_+) = \bC\langle c_{2k}\rangle$
 for all $k\ge 1$ (\cite[Theorem~1.4.3]{Fuks86};
 Goncharova~\cite{Goncharova73}).
\end{enumerate}
Consequently $\Theta_{3,\ell}$ is \emph{not} a quasi-isomorphism onto
the full scalar GF target: the chiral source has zero cohomology in
degrees $n\ge 3$, while the scalar GF target can carry unbounded
content. At chain level the complexes are already different before
cohomology, since the chiral complex is built from configuration-space
residues on~$X$ and the GF complex is a CE complex of the mode Lie
algebra.
\end{proposition}

\begin{proof}
Item~(i) is exactly the curve-level amplitude statement of
Theorem~H. Item~(ii) records that no mode-Hochschild vanishing theorem
is imported into this proposition. Item~(iii) is the
Goncharova--Fuks computation. The source cohomology of
$\Theta_{3,\ell}$ is zero above degree~$2$, whereas the scalar GF
classes $c_4,c_6,\ldots$ may survive. These classes therefore cannot
lie in the image of the chiral comparison map.
\end{proof}

\begin{remark}[Why Theorem~H does not extend to GF]
\label{rem:why-theorem-H-not-GF}
Theorem~H is the $[0,2]$ amplitude bound for chiral Hochschild on the
PBW-completed generic curve surface. The bound is not a bare formal
consequence of $\dim_\bC X=1$: it uses the ordered
Fulton--MacPherson collision-depth spectral sequence, the
pure-braid Orlik--Solomon contraction of the positive Arnold classes,
the PBW chiral Koszul comparison, the averaging step, and the
curve-level Verdier shift. GF cohomology is continuous Lie algebra
cohomology of the positive-mode algebra with a chosen coefficient
module; it has no FM collision filtration on~$X$ and no PBW/Arnold
contraction. Its unboundedness is therefore a feature, not a defect.
The same boundary excludes topological Hochschild homology,
categorical Hochschild cochains of dg/CY categories, and
product-ambient Hall Hochschild theories: their inputs are not chiral
algebras on the curve~$X$, and Theorem~H does not control their
cohomological amplitude.
\end{remark}

\section{Critical-level centres via Feigin--Frenkel}
\label{sec:critical-level-ff}

\begin{theorem}[Critical-level degree-zero comparison;
\ClaimStatusConditional]
\label{thm:critical-level-ff-center-unification}
\index{Feigin--Frenkel centre!degree-zero centre comparison}
\index{critical level!Hochschild centre comparison}
At the critical level $k = -h^\vee$ of the affine vertex algebra
$V_{-h^\vee}(\fg)$, the chiral centre and the associative mode centre
identify with the Feigin--Frenkel centre:
\[
 \ChirHoch^0(V_{-h^\vee}(\fg))
 \;\cong\;
 \HH^0(A_{\mathrm{mode}})
 \;\cong\;
 \mathrm{Fun}(\mathrm{Op}_{\fg^\vee}(D))
\]
where the right-hand side is the Feigin--Frenkel centre, the polynomial
ring of $\fg^\vee$-opers on the formal disk. Ordinary continuous
Gel'fand--Fuks degree-zero cohomology with trivial coefficients remains
$\mathbb C$; it matches the oper algebra only after replacing the
coefficient system by the critical central extension/oper coefficient
module. That coefficient replacement is the conditional part of the
comparison.
\end{theorem}

\begin{proof}
At the critical level, the Sugawara construction collapses and
$V_{-h^\vee}(\fg)$ is no longer Koszul; the Koszul locus hypothesis
of
Theorem~\ref{thm:three-hochschild-chain-level-agreement-low-degree}
fails. The first two degree-zero groups are centres of their native
algebras:
\begin{itemize}[nosep]
\item $\ChirHoch^0(V_{-h^\vee}(\fg)) = Z_{\mathrm{ch}}(V_{-h^\vee}(\fg))$
 equals the chiral centre, which Feigin--Frenkel
 \cite{FeFr92,Frenkel07} identify with
 $\mathrm{Fun}(\mathrm{Op}_{\fg^\vee}(D))$.
\item $\HH^0(A_{\mathrm{mode}}) = Z(A_{\mathrm{mode}})$ is the
 classical associative centre of the mode algebra; under the
 Feigin--Frenkel isomorphism the Segal--Sugawara generators of the
 mode centre match the oper-polynomial generators.
\item Ordinary $H^0_{\mathrm{cont}}(L_+;\bC)$ with trivial
 coefficients is $\bC$. The oper algebra appears only after passing
 to continuous cochains with coefficients in the critical central
 extension/oper module. The required splitting of the critical
 extension is not part of the ordinary GF complex and is kept as a
 conditional coefficient-change statement.
\end{itemize}
The first two identifications share the same Feigin--Frenkel target and
the same generators. The third agrees only after the stated coefficient
replacement, not as ordinary trivial-coefficient GF cohomology.
\end{proof}

\begin{remark}[Why the centre comparison is not a stronger equivalence]
\label{rem:ff-unification-degree-zero-only}
In higher degrees the comparison surfaces continue to differ at the
critical level. The classical $\HH^*$ of $A_{\mathrm{mode}}$ carries
its own Poisson structure, and ordinary scalar GF cohomology remains a
trivial-coefficient CE theory unless the coefficient system is
changed. The Feigin--Frenkel statement is a degree-zero centre
comparison, not a partial instance of a stronger equivalence and not a
Vol.~I theorem about CY categorical Hochschild or Hall Hochschild
objects.
\end{remark}

\begin{remark}[Chain vs cohomological boundary]
\label{rem:three-hochschild-chain-cohomology-boundary}
The boundary has three strata:
\begin{itemize}[nosep]
\item $n=0$: at critical level, the chiral centre and mode centre
 share the Feigin--Frenkel oper algebra; ordinary
 trivial-coefficient GF degree zero remains~$\bC$.
\item $n=1,2$ at non-critical level: chain-level quasi-isomorphism
 onto image via $\Theta_1,\Theta_{2,\ell},\Theta_{3,\ell}$ under the
 PBW and coefficient hypotheses.
\item $n\ge 3$: $H^n(\ChirHoch^\bullet)=0$ by Theorem~H, while
 scalar GF may continue unbounded. The vanishing is the reference-curve
 chiral Hochschild statement of
 Remark~\ref{rem:theorem-H-reference-curve-lane}; no uniform
 high-degree statement about $\HH^*_{\mathrm{mode}}$ is part of
 Vol.~I.
\end{itemize}
This is the sharp statement.
\end{remark}

\section{Formal-disk and cross-ambient boundary}
\label{sec:three-hochschild-consequences}

\begin{corollary}[Formal-disk comparison with fixed coefficients]
\label{cor:three-hochschild-scoped-comparison}
\ClaimStatusConditional
On the non-critical Koszul locus, the formal-disk comparison gives
chain maps
$\Theta_1,\Theta_{2,\ell},\Theta_{3,\ell}$
(Constructions~\ref{constr:theta1-chirhoch-to-HHmode},
\ref{constr:theta2-HHmode-to-GF},
\ref{constr:theta3-chirhoch-to-GF}) only after the PBW comparison,
quotient by the spectral-variable kernel, and coefficient datum~$\ell$
have been fixed. On $\tau_{\le 2}$ these maps are
quasi-isomorphisms onto their images. Above the curve-level amplitude,
Theorem~H gives
$H^n(\ChirHoch^\bullet(\cA))=0$ on the reference curve for
$n\ge 3$, while scalar GF may remain unbounded
(Proposition~\ref{prop:three-hochschild-high-degree-divergence}).

At critical level $k=-h^\vee$, the Feigin--Frenkel centre compares
the chiral centre and the mode centre in degree zero
(Theorem~\ref{thm:critical-level-ff-center-unification}); ordinary
trivial-coefficient GF degree zero remains~$\bC$ unless the coefficient
system is changed. No statement in this chapter identifies these
formal-disk shadows with categorical Hochschild cochains of a dg/CY
category or with product-ambient Hall Hochschild theories.
\end{corollary}

\begin{remark}[Cross-ambient boundary]
\label{rem:three-hochschild-propagation}
Volume~II may interpret the three formal-disk maps as boundary
truncation, commutator-Lie descent, and anomaly projection. That
interpretation is physical language for the same image statements, not
a new equivalence of Hochschild theories. Vol.~III uses categorical
Hochschild complexes of CY categories and Hall--Drinfeld double
constructions in their own ambient. A Stage--2 chiral specialisation
can produce a curve algebra to which Theorem~H applies, but the
categorical/Hall Hochschild object is not thereby a Vol.~I
consequence.
\end{remark}
