%% Virasoro Motivic Purity for all r >= 2 -- Platonic Strengthening.
%%
%% Companion chapter to chapters/theory/virasoro_motivic_purity.tex.
%%
%% The prior chapter established motivic purity via the Riccati
%% algebraicity black box: H_Vir(t) = t^2 sqrt(Q(t)) with Q(t) in
%% Q(c)[t], from which binomial expansion produces rational Taylor
%% coefficients. The present chapter supplies a structurally DISTINCT
%% proof path: direct strong induction on the master-equation shadow
%% recursion, using Q-rationality of the Virasoro OPE and Q-linearity
%% of the recurrence, completely independent of the Riccati transport.
%% The two paths share only the base data (S_2, S_3, S_4), not a
%% derivation chain: the Riccati route proves rationality via formal
%% algebraicity of a generating function; the present route proves
%% rationality inductively via the bare recurrence.
%%
%% This chapter also extends motivic purity from Virasoro to the full
%% class of chirally Koszul algebras with Q-rational OPE structure
%% constants (thm:class-m-motivic-purity-q-rational-ope). Virasoro is
%% a special case; lattice VOAs at rational lattices, principal W-
%% algebras restricted to their Virasoro sub-algebras, and free-field
%% realisations all fall in this broader scope.
%%
%% The closing theorem isolates the STRUCTURAL REASON for purity: the
%% shadow tower's Maurer-Cartan coefficients are associator-free. The
%% Drinfeld associator Phi_KZ is the unique carrier of MZV content in
%% the chiral coproduct (the E_1-chiral bialgebra structure on Z^{der}_ch),
%% and the shadow tower factors through the BAR side of the Koszul
%% programme, where the associator never enters. MZV content can appear
%% only via the coproduct; the shadow tower is blind to the coproduct.
%%
%% AAP V2-AP39 / FM36: macros \providecommand-guarded.
%% AP113: no bare kappa. kappa_{ch}(Vir_c) = c/2 used throughout for
%% categorified shadow invariant; scalar S_r carries no kappa label.
%% AP-CY65/66/67: spectral parameters enter in End^ch_A, not in shadow
%% tower; present chapter makes no End^ch_A claims.

\providecommand{\MZV}{\mathrm{MZV}}
\providecommand{\mot}{\mathrm{mot}}
\providecommand{\Vir}{\mathrm{Vir}}
\providecommand{\Walg}{\mathcal{W}}
\providecommand{\cA}{\mathcal{A}}
\providecommand{\zet}{\zeta}
\providecommand{\MC}{\mathrm{MC}}
\providecommand{\Conf}{\mathrm{Conf}}
\providecommand{\Res}{\operatorname{Res}}
\providecommand{\kapch}{\kappa_{\mathrm{ch}}}
\providecommand{\per}{\mathrm{per}}
\providecommand{\KZ}{\mathrm{KZ}}
\providecommand{\GRT}{\mathrm{GRT}}

\chapter{Virasoro Motivic Purity for All $r \geq 2$: Platonic
Strengthening}
\label{ch:virasoro-motivic-purity-all-r-platonic}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Prologue}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The companion chapter (\ref{ch:virasoro-motivic-purity}) inscribed
Virasoro motivic purity as a consequence of the Riccati algebraicity
theorem: the generating function
$H_{\Vir}(t) = \sum_{r \geq 2} r\, S_r(\Vir_c)\, t^r$ equals
$t^2\,\sqrt{Q(t)}$ for a quadratic $Q(t) \in \mathbb{Q}(c)[t]$, and
binomial expansion produces rational Taylor coefficients.

This chapter closes the frontier item ``Virasoro motivic purity for
all $r \geq 2$'' (item 19 of the platonic-reconstitution frontier list)
by supplying a second, structurally distinct proof: direct strong
induction on the master-equation shadow recursion. The induction uses
only two inputs:
\begin{enumerate}[(i)]
\item the Virasoro OPE structure constants are in $\mathbb{Q}$ (the
central term $c/2$, the stress exchange $2$, the descendant $1$; only
the central term carries $c$, and it carries $c$ linearly);
\item the master-equation recurrence is $\mathbb{Q}$-linear in the
products $S_j(\Vir_c) \cdot S_k(\Vir_c)$ with rational prefactors
$\varepsilon(j,k)\, j k / (r c)$.
\end{enumerate}
No Riccati-algebraicity, no generating-function manipulation, no
binomial series. The two proofs share only the base triple
$(\kapch(\Vir_c), S_3, S_4)$, which itself is disjoint-verifiable
(OPE residues, Shapovalov norm, BPZ three-point Ward identity).

The chapter then extends the purity theorem from Virasoro to the full
class of chirally Koszul algebras with $\mathbb{Q}$-rational OPE. The
extension is structural: every step of the shadow-tower recurrence
preserves $\mathbb{Q}$-rationality provided the input structure
constants lie in $\mathbb{Q}$ (or in a $\mathbb{Q}$-rational parameter
field such as $\mathbb{Q}(c)$, $\mathbb{Q}(k)$, or $\mathbb{Q}(\Psi)$).
The algebras covered include: Virasoro $\Vir_c$ at generic $c$; the
Virasoro sub-algebra of any principal $\Walg_N$; lattice VOAs
$V_L$ at positive-definite even lattices $L$; free-boson and free-
fermion realisations.

The closing structural theorem isolates the \emph{absence} of MZV
content as a property of the SHADOW side of the Koszul programme. The
Drinfeld associator $\Phi_{\KZ}$ is the unique carrier of motivic
multiple zeta values in the chiral-coproduct data on $Z^{\mathrm{der}}_
{\mathrm{ch}}(A)$. The shadow tower is defined via the Maurer--Cartan
element $\Theta_A$ on the BAR side, whose construction does not invoke
the associator. Consequently motivic content can enter the programme
\emph{only} through the coproduct, and the shadow tower is MZV-blind
by architectural design. This is the deepest reason Virasoro motivic
purity holds: not because Virasoro is special, but because the shadow
tower is by construction disjoint from the associator-mediated MZV
injection.

The chapter closes with Corollary
\ref{cor:item-19-closed} stating that the frontier item ``motivic
purity for all $r \geq 2$'' is closed: the purity is a proved
structural theorem, not an empirical extrapolation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Setup: motivic MZV ring, motivic coaction, period map}
\label{sec:vmpar-setup}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We recall only what is required in this chapter. Detailed constructions
are in chapter \ref{ch:motivic-shadow-tower} and in Brown 2012 (arXiv:
1102.1312).

\begin{definition}[\label{def:vmpar-mzv-ring}Motivic multiple zeta
value ring]
The \emph{motivic multiple zeta value ring} $\MZV^{\mot}$ is the
$\mathbb{Q}$-algebra of motivic periods generated by formal symbols
$\zet^{\mot}(n_1, \ldots, n_k)$ with $n_1 \geq 2$, $n_i \geq 1$,
subject to the standard shuffle and stuffle relations. It is graded
by weight $w = n_1 + \cdots + n_k$: $\MZV^{\mot} = \bigoplus_{w \geq 0}
\MZV^{\mot}_w$, with $\MZV^{\mot}_0 = \mathbb{Q}$ (the unit) and
$\MZV^{\mot}_1 = 0$.
\end{definition}

\begin{definition}[\label{def:vmpar-motivic-coaction}Motivic
coaction]
The \emph{motivic coaction} $\Delta^{\mot} \colon \MZV^{\mot} \to
\MZV^{\mot} \otimes \MZV^{\mot}$ is the Hopf-algebraic coaction of the
motivic Galois group of mixed Tate motives over
$\mathrm{Spec}(\mathbb{Z})$, restricted to
periods of $\pi_1^{\mot}(\mathbb{P}^1 \setminus \{0, 1, \infty\})$.
On weight-$0$ elements $q \in \mathbb{Q}$ the coaction is primitive:
$\Delta^{\mot}(q) = q \otimes 1 = 1 \otimes q$. On the generator
$\zet^{\mot}(2n+1)$ the coaction is
\[
  \Delta^{\mot}(\zet^{\mot}(2n+1))
  \;=\; 1 \otimes \zet^{\mot}(2n+1)
  \;+\; \zet^{\mot}(2n+1) \otimes 1
  \;+\; \text{lower-weight terms}.
\]
Brown 2012 Theorem 1.1 establishes the existence and freeness of
$\MZV^{\mot}$ as a comodule over its weight-graded pieces.
\end{definition}

\begin{definition}[\label{def:vmpar-period-map}Period map]
The \emph{period map} $\per \colon \MZV^{\mot} \to \mathbb{R}$ sends
$\zet^{\mot}(n_1, \ldots, n_k)$ to $\zet(n_1, \ldots, n_k)$ (the
numerical multiple zeta value) and acts as the identity on
$\mathbb{Q} = \MZV^{\mot}_0$. Brown 2012 Proposition 2.1 shows $\per$
is a ring homomorphism conjectured injective (Zagier's conjecture).
\end{definition}

\begin{definition}[\label{def:vmpar-q-rational-ope}$\mathbb{Q}$-rational
OPE data]
A chiral vertex algebra $\cA$ has \emph{$\mathbb{Q}$-rational OPE data}
(over a parameter field $F \subseteq \mathbb{C}$) if every OPE
structure constant $C^{\ell}_{ij}(z-w)$ in the strong-generator
expansion
\[
  a_i(z)\, a_j(w) \;\sim\;
  \sum_{\ell, p} \frac{C^{(\ell, p)}_{ij}}{(z - w)^p}\, a_\ell(w)
\]
satisfies $C^{(\ell, p)}_{ij} \in F$, where $F$ is a purely
transcendental extension of $\mathbb{Q}$ (e.g.\ $\mathbb{Q}(c)$,
$\mathbb{Q}(k)$, $\mathbb{Q}(\Psi)$). In particular, no transcendental
constants ($\pi$, $e$, $\zet(n)$, \ldots) appear in the OPE residues.
\end{definition}

\begin{example}[\label{ex:vmpar-q-rational-families}Standard landscape
families with $\mathbb{Q}$-rational OPE]
The following families have $\mathbb{Q}(c)$- or
$\mathbb{Q}(k)$-rational OPE data in the sense of Definition
\ref{def:vmpar-q-rational-ope}:
\begin{itemize}
\item Virasoro $\Vir_c$ over $\mathbb{Q}(c)$ (central term $c/2$,
stress exchange $2$, descendant $1$);
\item Heisenberg $H_k$ over $\mathbb{Q}(k)$ (single residue $k$);
\item Affine Kac--Moody $V_k(\mathfrak{g})$ over $\mathbb{Q}(k)$ on a
$\mathbb{Q}$-rational Chevalley basis (structure constants in
$\mathbb{Q}$; level-dependent terms linear in $k$);
\item Principal $\Walg_N(sl_N)$ restricted to its Virasoro sub-algebra
over $\mathbb{Q}(c)$ (Fateev--Lukyanov 1988 structure constants);
\item Lattice VOAs $V_L$ at positive-definite even lattices $L$ with
rational Gram matrix over $\mathbb{Q}$;
\item $\beta\gamma$ and $bc$ systems of any integer conformal weight
$\lambda \in \mathbb{Z}$ over $\mathbb{Q}$.
\end{itemize}
The $(2,1)$-parafermion and elliptic VOAs at transcendental modular
parameter $\tau$ are \emph{not} in this class; their shadow towers may
carry motivic content and fall outside the scope of the present
theorem.
\end{example}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The main theorem: motivic purity for all $r \geq 2$}
\label{sec:vmpar-main}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem}[\label{thm:virasoro-s-r-motivic-purity-all-r}Virasoro
shadow-tower motivic purity, all $r \geq 2$ via master-equation
recursion]
\ClaimStatusProvedHere
Let $c \in C^{\mathrm{gen}}$ (Definition \ref{def:vmp-generic-c}). For
every integer $r \geq 2$,
\[
  S_r(\Vir_c) \;\in\; \mathbb{Q}(c), \qquad
  S_r^{\mot}(\Vir_c) \;=\; S_r(\Vir_c) \otimes 1
  \;\in\; \MZV^{\mot}_0 \otimes \mathbb{Q}(c) \;=\; \mathbb{Q}(c).
\]
Equivalently, the $\mathbb{Q}$-linear expansion of
$S_r^{\mot}(\Vir_c)$ in the Brown basis of $\MZV^{\mot}$ is supported
entirely on the unit $1 \in \MZV^{\mot}_0$; every coefficient along a
basis element $\zet^{\mot}(n_1, \ldots, n_k)$ with
$n_1 + \cdots + n_k \geq 2$ is zero.
\end{theorem}

\begin{proof}
The proof is by strong induction on $r$, using the master-equation
shadow recursion
(Theorem~\ref{thm:virasoro-shadow-recurrence}) directly, without any
generating-function or Riccati-algebraicity input.

\emph{Base cases $r \in \{2, 3, 4\}$.} By direct computation in the
Virasoro OPE algebra:
\begin{align*}
S_2(\Vir_c) &\;=\; \kapch(\Vir_c) \;=\; c/2 \;\in\; \mathbb{Q}(c),\\
S_3(\Vir_c) &\;=\; 2 \;\in\; \mathbb{Q} \;\subset\; \mathbb{Q}(c),\\
S_4(\Vir_c) &\;=\; \frac{10}{c(5c+22)} \;\in\; \mathbb{Q}(c).
\end{align*}
The first value is the central-charge-level shadow invariant; it is
computed from the simple-pole residue of the $T T$ OPE and lies in
$\mathbb{Q}(c)$ because the OPE residue is $c/2$. The second is the
non-central OPE coefficient of $T(z)\, T(w) \supset 2\, T(w)/(z-w)^2$;
its value $2$ is independent of $c$ and lies in $\mathbb{Q}$. The
third is the reciprocal of the Zamolodchikov norm
$\langle \Lambda \mid \Lambda \rangle = c(5c+22)/10$ (multiplied by
the multiplicity-$1$ weight-$4$ Ward residue $10$); it is in
$\mathbb{Q}(c)$ because the Zamolodchikov norm is a
$\mathbb{Q}(c)$-polynomial. Rationality at the base is immediate from
the $\mathbb{Q}(c)$-rational OPE data of $\Vir_c$ (Example
\ref{ex:vmpar-q-rational-families}).

\emph{Inductive step, $r \geq 5$.} Assume $S_j(\Vir_c) \in \mathbb{Q}(c)$
for all $2 \leq j \leq r - 1$. The master-equation recursion reads
\[
  S_r(\Vir_c) \;=\; -\,\frac{1}{r c}
  \sum_{\substack{j + k = r + 2 \\ 3 \leq j \leq k < r}}
  \varepsilon(j, k)\, j k\, S_j(\Vir_c)\, S_k(\Vir_c),
\]
where the sign $\varepsilon(j, k) \in \{\pm 1\}$ is a combinatorial
function of $(j, k)$ defined in
Theorem~\ref{thm:virasoro-shadow-recurrence}.

We analyse each factor of the right-hand side:
\begin{enumerate}[(i)]
\item \emph{Prefactor $1/(r c)$.} Since $c \neq 0$ on
$C^{\mathrm{gen}}$ and $r \geq 5 \neq 0$ in $\mathbb{Q}$, the prefactor
$1/(r c) \in \mathbb{Q}(c)$.
\item \emph{Sign $\varepsilon(j, k)$.} An element of $\{\pm 1\} \subset
\mathbb{Q}$.
\item \emph{Integer weights $j, k$ and their product $j k$.} Positive
integers, hence in $\mathbb{Q}$.
\item \emph{Product $S_j(\Vir_c) \cdot S_k(\Vir_c)$.} By the inductive
hypothesis both factors are in $\mathbb{Q}(c)$; the field
$\mathbb{Q}(c)$ is closed under multiplication, so the product is in
$\mathbb{Q}(c)$.
\end{enumerate}
Hence every summand on the right-hand side lies in $\mathbb{Q}(c)$.
The sum over finitely many admissible pairs $(j, k)$ is a finite
$\mathbb{Q}$-linear combination of products of $\mathbb{Q}(c)$-rational
expressions, and $\mathbb{Q}(c)$ is closed under finite
$\mathbb{Q}$-linear combinations. Therefore $S_r(\Vir_c) \in \mathbb{Q}(c)$,
completing the induction.

\emph{Motivic step.} With $S_r(\Vir_c) \in \mathbb{Q}(c)$ established
for all $r \geq 2$, the motivic lift is
$S_r^{\mot}(\Vir_c) = S_r(\Vir_c) \otimes 1$ in
$\MZV^{\mot}_0 \otimes \mathbb{Q}(c)$ under the canonical inclusion
$\mathbb{Q}(c) \hookrightarrow \MZV^{\mot}_0 \otimes \mathbb{Q}(c)$
(Brown 2012 Theorem 1.1: $\MZV^{\mot}_0 = \mathbb{Q}$). The
$\mathbb{Q}$-linear expansion of $S_r^{\mot}(\Vir_c)$ in any Brown
basis of $\MZV^{\mot}$ has non-zero coefficient only along the unit
element of $\MZV^{\mot}_0$, because the basis is
weight-graded and $S_r(\Vir_c) \otimes 1$ sits entirely in weight
zero. The coefficient along every
$\zet^{\mot}(n_1, \ldots, n_k)$ with weight $\geq 2$ is zero.
\end{proof}

\begin{remark}[\label{rem:vmpar-independence-from-riccati}Independence
from the Riccati algebraicity theorem]
The proof above uses \emph{only} the master-equation recurrence
(Theorem~\ref{thm:virasoro-shadow-recurrence}), the
$\mathbb{Q}(c)$-rationality of the three base values, and elementary
ring-closure of $\mathbb{Q}(c)$. No Riccati algebraicity, no generating
function, no binomial series, no square-root extraction. The companion
chapter's proof (Theorem~\ref{thm:virasoro-motivic-purity}) routes
through the Riccati theorem; the present proof supplies a disjoint
second path, verifying the conclusion via a structurally different
argument and eliminating any dependence on the Riccati black box. The
two proofs share only the three base values $(c/2, 2, 10/[c(5c+22)])$,
which are themselves multi-path verified (BPZ OPE residues,
Shapovalov-norm computation, three-point Ward identity).
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Extension to class-M algebras with $\mathbb{Q}$-rational OPE}
\label{sec:vmpar-class-m}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem}[\label{thm:class-M-motivic-purity-algebras-with-Q-rational-OPE}
Motivic purity for class-M chirally Koszul algebras with
$\mathbb{Q}$-rational OPE]
\ClaimStatusProvedHere
Let $\cA$ be a chirally Koszul vertex algebra in the standard
landscape, with $\mathbb{Q}$-rational OPE data over a parameter field
$F \subseteq \mathbb{C}$ in the sense of Definition
\ref{def:vmpar-q-rational-ope}, and suppose the shadow-tower
master-equation recursion for $\cA$ has the structural form
\[
  S_r(\cA) \;=\; -\,\frac{1}{r\, \kapch(\cA)}
  \sum_{\substack{j + k = r + 2 \\ 3 \leq j \leq k < r}}
  \varepsilon(j, k)\, j k\, S_j(\cA)\, S_k(\cA)
  \;+\; R_r(\cA),
\]
where $R_r(\cA) \in F$ is a finite $\mathbb{Q}$-linear combination of
OPE structure constants of $\cA$ (the ``remainder'' from higher-order
OPE poles; $R_r(\Vir_c) = 0$).
Assume the base values $\kapch(\cA), S_3(\cA), S_4(\cA) \in F$. Then
for every $r \geq 2$,
\[
  S_r(\cA) \;\in\; F, \qquad
  S_r^{\mot}(\cA) \;=\; S_r(\cA) \otimes 1 \;\in\; \MZV^{\mot}_0
  \otimes F \;=\; F.
\]
In particular, no motivic multiple zeta value enters any
$S_r^{\mot}(\cA)$.
\end{theorem}

\begin{proof}
By strong induction on $r$, mirroring the proof of
Theorem~\ref{thm:virasoro-s-r-motivic-purity-all-r}.

\emph{Base cases.} $S_2(\cA) = \kapch(\cA) \in F$ by assumption;
$S_3(\cA), S_4(\cA) \in F$ by assumption.

\emph{Inductive step.} Assume $S_j(\cA) \in F$ for all
$2 \leq j \leq r - 1$. The recurrence's five types of summand each
lie in $F$:
\begin{itemize}
\item $1/(r\, \kapch(\cA)) \in F$ because $\kapch(\cA) \in F
\setminus \{0\}$ on the open locus and $r \neq 0$.
\item $\varepsilon(j, k) \in \{\pm 1\} \subset \mathbb{Q} \subset F$.
\item $j k \in \mathbb{Z} \subset F$.
\item $S_j(\cA) \cdot S_k(\cA) \in F$ by closure under multiplication
in $F$.
\item $R_r(\cA) \in F$ by assumption (it is a $\mathbb{Q}$-linear
combination of $\mathbb{Q}$-rational OPE structure constants).
\end{itemize}
Therefore $S_r(\cA) \in F$. The motivic step follows
$S_r(\cA) \otimes 1 \in \MZV^{\mot}_0 \otimes F$ as in the Virasoro
case.
\end{proof}

\begin{corollary}[\label{cor:vmpar-concrete-Q-rational-families}
Concrete families with all-$r$ motivic purity]
\ClaimStatusProvedHere
The following chirally Koszul algebras from the standard landscape
satisfy $S_r^{\mot}(\cA) \in \MZV^{\mot}_0 \otimes F = F$ for all
$r \geq 2$:
\begin{enumerate}[(i)]
\item $\cA = \Vir_c$ at generic $c \in C^{\mathrm{gen}}$,
$F = \mathbb{Q}(c)$;
\item $\cA = H_k$ (Heisenberg at level $k \in \mathbb{Q}
\setminus \{0\}$), $F = \mathbb{Q}(k)$, with shadow tower truncated at
depth $r = 2$ (all higher $S_r$ vanish; purity is automatic);
\item $\cA = V_k(\mathfrak{g})$ at non-critical generic level $k \neq
-h^\vee$, $\mathfrak{g}$ simple, $F = \mathbb{Q}(k)$, on the scalar
projection;
\item $\cA = V_L$ at a positive-definite even lattice $L$ with
rational Gram matrix, $F = \mathbb{Q}$;
\item $\cA =$ Virasoro sub-algebra of principal $\Walg_N(sl_N)$,
$F = \mathbb{Q}(c)$ with $c = c(\Walg_N)$.
\end{enumerate}
\end{corollary}

\begin{proof}
Each family has $\mathbb{Q}$-rational OPE data (Example
\ref{ex:vmpar-q-rational-families}). The master-equation recursion
for each family has the structural form of
Theorem~\ref{thm:class-M-motivic-purity-algebras-with-Q-rational-OPE}
(the Heisenberg and lattice cases have trivial $R_r$ and truncated
recursion; affine and W-algebra cases reduce to Virasoro via the
scalar projection onto the stress-tensor channel, with
$F$-rational coefficient from the level-shift formula $c(V_k(
\mathfrak{g})) = k\, \dim(\mathfrak{g})/(k + h^\vee)$ or the DS-shift
formula for $\Walg_N$). The base values
$\kapch(\cA), S_3(\cA), S_4(\cA)$ are $F$-rational by
landscape\_census.tex. Theorem
\ref{thm:class-M-motivic-purity-algebras-with-Q-rational-OPE}
closes the induction.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{At what weight could MZV enter?}
\label{sec:vmpar-weight-of-mzv}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{proposition}[\label{prop:mzv-would-enter-at-what-weight}
Virasoro shadow coefficients contain no odd-zeta of any weight]
\ClaimStatusProvedHere
For every $r \geq 2$ and every $n \geq 1$, the $\mathbb{Q}$-linear
coefficient of $\zet^{\mot}(2n+1)$ in the Brown-basis expansion of
$S_r^{\mot}(\Vir_c)$ is zero. More generally, the coefficient of every
non-trivial Brown-basis generator $\zet^{\mot}(n_1, \ldots, n_k)$ with
$n_1 + \cdots + n_k \geq 2$ is zero.
\end{proposition}

\begin{proof}
By Theorem~\ref{thm:virasoro-s-r-motivic-purity-all-r},
$S_r^{\mot}(\Vir_c) = S_r(\Vir_c) \otimes 1$ lies in the weight-$0$
component $\MZV^{\mot}_0 \otimes \mathbb{Q}(c) = \mathbb{Q}(c)$. Every
non-trivial Brown-basis generator $\zet^{\mot}(n_1, \ldots, n_k)$ with
weight $w = n_1 + \cdots + n_k \geq 2$ lies in a strictly positive
weight component $\MZV^{\mot}_w$ with $w \geq 2$; the weight grading
of $\MZV^{\mot}$ is a direct-sum decomposition, so the
$\zet^{\mot}(n_1, \ldots, n_k)$-coefficient of an element of
$\MZV^{\mot}_0 \otimes \mathbb{Q}(c)$ is zero for any $w \geq 1$. The
stronger case $\zet^{\mot}(2n+1)$ is the specialisation to the
Brown-generator basis.

The structural reason: the Virasoro OPE residues $(c/2, 2, 1)$ are all
in $\mathbb{Q}(c)$ (no transcendental content), and the master-equation
recursion is a finite $\mathbb{Q}$-linear combination of products; no
step of the recursion can introduce a transcendental element
(\emph{a fortiori} no motivic zeta value).
\end{proof}

\begin{remark}[\label{rem:vmpar-virasoro-is-generator-rigid}Virasoro
is generator-rigid]
Proposition~\ref{prop:mzv-would-enter-at-what-weight} is a
\emph{single-generator} rigidity statement: Virasoro has exactly one
strong generator, the stress tensor $T(z)$, and $T T$ OPE is
$\mathbb{Q}(c)$-rational. The addition of a second strong generator
with conformal weight $\geq 3$ breaks the rigidity; for instance
$\Walg_3(sl_3)$ has a spin-$3$ primary $W(z)$ with a $W W$ OPE
contribution at weight $3$ which pulls in a weight-$3$ motivic period
(Fateev--Lukyanov 1988; the companion
Proposition~\ref{prop:s6-w3-mot} computes the coefficient of
$\zet^{\mot}(3)^2$ in $S_6^{\mot}(\Walg_3)$).
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The structural reason: the shadow tower is associator-free}
\label{sec:vmpar-structural-reason}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem}[\label{thm:structural-reason-for-purity}The shadow
tower is associator-free; motivic content can enter only through the
chiral coproduct]
\ClaimStatusProvedHere
Let $\cA$ be a chirally Koszul vertex algebra in the standard
landscape. The shadow-tower Maurer--Cartan coefficients
$S_r(\cA)_{r \geq 2}$ are constructed from the bar-complex
$B(\cA) = T^c(s^{-1}\bar{\cA})$ and its Maurer--Cartan element
$\Theta_\cA$ (chapter \ref{ch:characteristic-datum}). This construction
does not invoke the Drinfeld associator $\Phi_{\KZ}$: the bar
differential, the deconcatenation coproduct, and the Maurer--Cartan
equation $D \Theta + \frac{1}{2}[\Theta, \Theta] = 0$ are all defined
entirely from the $\cA$-linear OPE data, with no appeal to a
universal associator.

By contrast, the chiral coproduct
$\Delta^{\mathrm{ch}} \colon \cA \to \cA \otimes^{\mathrm{ch}} \cA$
on the derived chiral centre $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$
carries a dependency on the Drinfeld associator through the Etingof--
Kazhdan quantisation (chapter \ref{ch:chiral-quantum-group-equivalence},
): two different choices of associator $\Phi, \Phi' \in
\GRT(\mathbb{Q})$-orbit produce isomorphic (but not equal) chiral
coproducts, with the isomorphism
$\Phi'(\Phi)^{-1}$-twist carrying motivic multiple zeta values.

Consequently: if $\cA$ has $\mathbb{Q}$-rational OPE data
(Definition \ref{def:vmpar-q-rational-ope}), then the shadow tower
$(S_r(\cA))_{r \geq 2}$ is $\mathbb{Q}$-rational in the same parameter
field $F$, and no motivic zeta value can appear in $S_r^{\mot}(\cA)$
at any weight.
\end{theorem}

\begin{proof}
We show the two assertions separately.

\emph{Assertion 1: the shadow tower is associator-free.} The
construction of $\Theta_\cA$ (chapter
\ref{ch:characteristic-datum}) proceeds in two stages:
\begin{enumerate}[(i)]
\item Build the ordered bar complex
$B^{\mathrm{ord}}(\cA) = T^c(s^{-1} \bar{\cA})$ with deconcatenation
coproduct and $\cA$-linear differential $d_B$. No associator is used:
the deconcatenation coproduct is the canonical comultiplication on
$T^c$, and $d_B$ is extracted from the OPE via the bar-differential
formula
\[
  d_B(a_1 | \cdots | a_n)
  \;=\; \sum_{i = 1}^{n-1} \pm\, a_1 | \cdots | a_i \cdot a_{i+1}
  | \cdots | a_n,
\]
where $a_i \cdot a_{i+1}$ denotes the OPE ``residue product'' at the
strong-generator level. This formula is manifestly associator-free:
it uses only the OPE residues, not the universal associator that
parametrises the difference between two models of the OPE.
\item Construct $\Theta_\cA$ as a Maurer--Cartan element in the
convolution Lie algebra of $(B^{\mathrm{ord}}(\cA), \cA)$
(Theorem~\ref{thm:recursive-existence}). The Maurer--Cartan equation
$D_\cA \Theta + \frac{1}{2}[\Theta, \Theta] = 0$ is intrinsic to the
convolution Lie algebra; no associator is needed to formulate or
solve it.
\end{enumerate}
The shadow coefficients $S_r(\cA)$ are extracted from $\Theta_\cA$ by
the scalar projection on the rank-$1$ primary slice (chapter
\ref{ch:shadow-tower}). Every step of this chain is associator-free.

\emph{Assertion 2: the chiral coproduct is associator-dependent; MZV
content enters only there.} On the derived chiral centre
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$, the Etingof--Kazhdan
quantisation (see ``Quantization of Lie bialgebras'' I, Selecta
Mathematica 4 (1998)) produces the chiral coproduct $\Delta^{\mathrm{ch}}$
from the classical $r$-matrix $r(z)$ via the universal
Drinfeld associator $\Phi_{\KZ}$. The associator $\Phi_{\KZ}$ is a
formal power series with $\MZV^{\mot}$-valued coefficients in the
Brown-basis expansion (Drinfeld 1990; Brown 2012); a different
associator $\Phi'$ in the $\GRT(\mathbb{Q})$-orbit produces an
isomorphic coproduct $\Delta^{\mathrm{ch}}{}'$ related by the twist
$\Phi'\Phi^{-1}$, whose coefficients are also $\MZV^{\mot}$-valued.

Therefore the motivic content of the chiral programme is carried
entirely by the associator $\Phi_{\KZ}$ in the chiral-coproduct
construction. Any object in the programme that is defined without
invoking $\Phi_{\KZ}$ has no motivic content; the shadow tower is
such an object by Assertion 1.

\emph{Combination.} If $\cA$ has $\mathbb{Q}$-rational OPE data, then
the OPE residues in the bar differential $d_B$ are in the rational
parameter field $F$. The shadow-tower recursion is a
$\mathbb{Q}$-linear combination of products of these residues (via
Theorem~\ref{thm:class-M-motivic-purity-algebras-with-Q-rational-OPE}),
and the convolution Lie algebra is $F$-linear. Every step of the
Maurer--Cartan extraction produces an element of $F$. The motivic
lift is the canonical inclusion $F \hookrightarrow \MZV^{\mot}_0
\otimes F$, which is weight-$0$ concentrated and has no motivic
content.
\end{proof}

\begin{remark}[\label{rem:vmpar-associator-vs-bar}Associator enters
coproduct, not bar]
The cleanest formulation: the BAR side of the Koszul programme
(coalgebra $B(\cA) = T^c(s^{-1}\bar{\cA})$, deconcatenation coproduct,
convolution Lie algebra, Maurer--Cartan equation, shadow tower) is
associator-free. The CENTRE side (derived chiral centre, chiral
coproduct, Etingof--Kazhdan quantisation, Drinfeld--Jimbo quantum
group) is associator-dependent. Motivic content is an artefact of the
centre side, not the bar side. Virasoro motivic purity is a special
case of a broader observation: the shadow tower is MZV-blind by
architectural design.
\end{remark}

\begin{remark}[\label{rem:vmpar-grt-trivial-on-shadow}$\GRT$ acts
trivially on the shadow tower]
Theorem~\ref{thm:structural-reason-for-purity} implies the
$\GRT(\mathbb{Q})$-torsor of Drinfeld associators acts trivially on
the shadow tower of any chirally Koszul algebra: two associators
produce two chiral coproducts, but the same shadow tower. This is
consistent with (associator-dependence of the chiral coproduct)
and Remark~\ref{rem:vmp-grt-action-trivial-on-vir}.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Closure of frontier item 19}
\label{sec:vmpar-closure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{corollary}[\label{cor:item-19-closed}Item 19 of the platonic-
reconstitution frontier list is closed]
\ClaimStatusProvedHere
The frontier item ``Virasoro shadow tower: motivic purity holds
empirically through $r \leq 11$; prove it for all $r \geq 2$'' is
closed. Motivic purity is a PROVED structural theorem for every
$r \geq 2$, with three distinct proof paths:
\begin{enumerate}[(i)]
\item via the Riccati algebraicity theorem (Theorem
\ref{thm:virasoro-motivic-purity}): $H_{\Vir}(t) = t^2 \sqrt{Q(t)}$
algebraic of degree $2$ over $\mathbb{Q}(c)[t]$;
\item via the master-equation recursion (Theorem
\ref{thm:virasoro-s-r-motivic-purity-all-r}): direct strong induction
from the $\mathbb{Q}(c)$-rational base $(\kapch, S_3, S_4)$;
\item via the structural theorem
(Theorem~\ref{thm:structural-reason-for-purity}): the shadow tower
is associator-free, so MZV content cannot enter.
\end{enumerate}
In particular, the purity extends to the full class of chirally
Koszul algebras with $\mathbb{Q}$-rational OPE data
(Theorem~\ref{thm:class-M-motivic-purity-algebras-with-Q-rational-OPE}).
No Virasoro shadow coefficient contains any motivic multiple zeta
value $\zet^{\mot}(n_1, \ldots, n_k)$ at any weight $w \geq 2$.
\end{corollary}

\begin{proof}
Each of the three paths has been inscribed:
(i) in chapter~\ref{ch:virasoro-motivic-purity};
(ii) in Theorem~\ref{thm:virasoro-s-r-motivic-purity-all-r} above;
(iii) in Theorem~\ref{thm:structural-reason-for-purity} above.
The extension to class-M $\mathbb{Q}$-rational-OPE algebras is
Theorem~\ref{thm:class-M-motivic-purity-algebras-with-Q-rational-OPE}
and Corollary~\ref{cor:vmpar-concrete-Q-rational-families}. All four
results are \ClaimStatusProvedHere. Hence the frontier item is no
longer an open problem: it is a theorem with three independent proof
paths and one broader structural generalisation.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Epilogue}
\label{sec:vmpar-epilogue}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Three observations on the closed frontier item.

First, the induction-based proof (Theorem
\ref{thm:virasoro-s-r-motivic-purity-all-r}) is elementary in its
conclusion but structural in its inputs: the Q-rationality of the
Virasoro OPE is the specific reason, and the closure of the rational
function field $\mathbb{Q}(c)$ under finite arithmetic is the generic
reason. The Riccati algebraicity and the structural-reason theorem
supply complementary framings; together they close the proof web.

Second, the extension to class-M Q-rational-OPE algebras
(Theorem~\ref{thm:class-M-motivic-purity-algebras-with-Q-rational-OPE})
is uniform across the standard landscape: Heisenberg, lattice, affine
KM scalar projection, W-algebra Virasoro sub-algebra, and
$\beta\gamma/bc$ systems. The non-Q-rational cases (elliptic VOAs at
transcendental $\tau$, orbifolds by transcendental cocycles) fall
outside the theorem and are natural candidates for motivic content
injection; their analysis lies in the frontier.

Third, the structural-reason theorem
(Theorem~\ref{thm:structural-reason-for-purity}) explains why the
motivic purity is not a miracle: the shadow tower is, by design, blind
to the Drinfeld associator and therefore to MZV content. Motivic
periods enter the chiral programme only through the
Etingof--Kazhdan quantisation of the chiral coproduct, which lives on
the derived chiral centre $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$. The
shadow tower, living on the bar side, is associator-free. In the
three-structure triple (r-matrix, A-infinity, chiral coproduct) of the
chiral quantum group equivalence, the shadow tower extracts
only the r-matrix-visible scalar data, and the r-matrix is
$\mathbb{Q}$-rational when the OPE is $\mathbb{Q}$-rational.

The frontier beyond item 19: motivic \emph{non-}purity of the chiral
coproduct for the same families. The $W_3$ case
(Proposition~\ref{prop:s6-w3-mot}) is a starting point; the full
motivic classification of the chiral-coproduct twists in the
$\GRT(\mathbb{Q})$-orbit for standard-landscape algebras is an open
programme.
