%% Virasoro Motivic Purity.
%%
%% Inscribes the theorem that every Virasoro shadow-tower coefficient
%% S_r(Vir_c) is a rational function of c and that its motivic lift
%% carries no multiple-zeta-value contribution. The upstream chapter
%% motivic_shadow_tower.tex (Section 4, Propositions prop:s4-vir-mot
%% and prop:s5-vir-mot) verified rationality at r = 4, 5 by direct
%% substitution and cited the cohomological vanishing argument at the
%% level of a remark; this theorem upgrades the statement to a
%% theorem valid for all r >= 2 via the Riccati shadow-transport
%% operator (Theorem thm:riccati-algebraicity,
%% higher_genus_modular_koszul.tex).
%%
%% Scope: Virasoro Vir_c on the Koszul locus (generic c; the excluded
%% minimal-model points c = c_{p,q} = 1 - 6(p - q)^2 / (p q) are
%% treated separately and their shadow tower vanishes identically in
%% the admissible weights by Feigin-Fuchs cohomology). The companion
%% chapter motivic_shadow_tower.tex Proposition prop:s6-w3-mot remains
%% valid only as a period-boundary statement: a spin-3 primary supplies
%% a possible Arnold/KZ source, not a non-zero zeta coefficient. Section
%% 6 makes the comparison explicit (cf. remark rem:vir-vs-w3-contrast).
%%
%% Macros are \providecommand-guarded.
%% No bare kappa: the central-charge-level shadow invariant is
%% written kappa_{ch}(Vir_c) = c/2 throughout; the generic shadow
%% coefficient S_r(Vir_c) has no kappa label (it is a scalar rational
%% function, not a categorical invariant).

\providecommand{\MZV}{\mathrm{MZV}}
\providecommand{\mot}{\mathrm{mot}}
\providecommand{\num}{\mathrm{num}}
\providecommand{\rat}{\mathrm{rat}}
\providecommand{\Vir}{\mathrm{Vir}}
\providecommand{\Walg}{\mathcal{W}}
\providecommand{\cA}{\mathcal{A}}
\providecommand{\cW}{\mathcal{W}}
\providecommand{\wt}{\mathrm{wt}}
\providecommand{\zet}{\zeta}
\providecommand{\MC}{\mathrm{MC}}
\providecommand{\Conf}{\mathrm{Conf}}
\providecommand{\Res}{\operatorname{Res}}
\providecommand{\kapch}{\kappa_{\mathrm{ch}}}

\chapter{Virasoro Motivic Purity}
\label{ch:virasoro-motivic-purity}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Prologue}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The motivic shadow-tower programme (chapter
\ref{ch:motivic-shadow-tower}) verified rationality of the first
four Virasoro shadow coefficients,
\[
 S_2(\Vir_c) = \tfrac{c}{2}, \qquad
 S_3(\Vir_c) = 2, \qquad
 S_4(\Vir_c) = \tfrac{10}{c(5c + 22)}, \qquad
 S_5(\Vir_c) = \tfrac{-48}{c^2(5c + 22)},
\]
by direct substitution in the master-equation recursion and by
independent Wick-reduction at $r = 5$. At $r = 4, 5$ the absence of
motivic multiple zeta values was an observation, not a theorem:
Propositions~\ref{prop:s4-vir-mot} and \ref{prop:s5-vir-mot} proved
rational values, but the extrapolation to all $r \geq 2$ was stated
as a remark (Remark~\ref{rem:w3-first-zeta3}, citing Feigin--Fuchs
cohomology vanishing).

This chapter closes the extrapolation for the weighted Riccati-metric
normalization. The mechanism is not
cohomological vanishing at each weight separately; it is the
Riccati algebraicity of the shadow generating function
$H^{\rm wt}(t) = \sum_{r \geq 2} r\, \widehat S^{\rm wt}_r(\Vir_c)\, t^r$
(Theorem~\ref{thm:riccati-algebraicity}, proved in
higher\_genus\_modular\_koszul.tex). For Virasoro on a one-dimensional
primary slice, $H^{\rm wt}(t)$ satisfies
$(H^{\rm wt}(t))^2 = t^4\, Q(t)$ with
$Q(t) \in \mathbb{Q}(c)[t]$ a quadratic polynomial determined
entirely by $(\kapch(\Vir_c), S_3, S_4) = (c/2,\, 2,\, 10/[c(5c+22)])$.
Taylor-expanding $H^{\rm wt}(t) = t^2\,\sqrt{Q(t)}$ around $t = 0$
keeps every weighted coefficient in the rational field
$\mathbb{Q}(c)$. The manuscript coefficients are treated by the
finite-recurrence argument in
Chapter~\ref{ch:virasoro-motivic-purity-all-r-platonic}.

The motivic consequence is immediate. The only mechanism by which a
motivic multiple zeta value $\zet^{\mot}(n_1, \ldots, n_k)$ could
enter $\widehat S^{\rm wt,\mot}_r(\Vir_c)$ is via an Arnold period on
$\Conf_r(\mathbb{C})$ that survives the averaging map and carries a
non-trivial weight-$(n_1 + \cdots + n_k)$ motivic content. The
Riccati transport tells us no such period enters in the weighted
normalization: the generating function $H^{\rm wt}(t)$ is algebraic of
degree $2$ over
$\mathbb{Q}(c)[t]$, and algebraic functions have rational Taylor
coefficients. Hence the period map
$\per \colon \MZV^{\mot} \to \mathbb{R}$ restricted to
$\widehat S^{\rm wt,\mot}_r(\Vir_c)$ is trivial: the motivic lift
equals $\widehat S^{\rm wt}_r(\Vir_c) \otimes 1 \in \mathbb{Q}(c)
\subset \MZV^{\mot}_0 \otimes \mathbb{Q}(c)$.

The W-algebra picture sharpens the boundary. At $W_3$ and shadow degree
$6$ (Proposition~\ref{prop:s6-w3-mot}), a spin-$3$ primary supplies the
first local channel in which an Arnold/KZ period can occur. This does
not prove that a $\zet^{\mot}(3)$ coefficient survives the
ordered-to-symmetric averaging map. Virasoro has no such spin-$3$
primary; every generator is the stress tensor $T(z)$, whose OPE is
rational. The absence of non-stress-tensor primaries on Virasoro is
precisely why the Riccati transport closes on the first three
invariants $(\kapch, S_3, S_4)$ and produces rational output at every
weight.

The chapter is organised as follows.
Section~\ref{sec:vmp-setup} fixes the setup and recalls the Riccati
algebraicity. Section~\ref{sec:vmp-main} states the purity
theorem. Section~\ref{sec:vmp-denominator} proves the weighted
denominator bound $c^{r-3}(5c + 22)^{\lfloor (r-2)/2 \rfloor}$.
Section~\ref{sec:vmp-transport}
records the Riccati-transport preservation of rationality as a
stand-alone theorem. Section~\ref{sec:vmp-no-mzv} gives the motivic
coaction corollary: triviality on
$\widehat S^{\rm wt,\mot}_r(\Vir_c)$.
Section~\ref{sec:vmp-w-algebra-comparison} compares Virasoro to $W_3$
and records the conditional finite-lane propagation along the
Drinfeld--Sokolov stress-tensor projection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Setup: shadow tower, Riccati transport, motivic lift}
\label{sec:vmp-setup}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We recall only what is required. The shadow tower
$\{S_r(\cA)\}_{r \geq 2}$ is defined in the characteristic-datum
part (\ref{part:characteristic-datum}) as the sequence of
$\MC$-coefficients of the universal Maurer--Cartan element
$\Theta_{\cA}$ in the ordered convolution $E_1$ dGLA. For the
Virasoro chiral algebra $\Vir_c$ at generic central charge $c$, the
shadow tower is the sequence of scalar rational coefficients obtained
from the single-line primary slice generated by the stress tensor
$T(z)$ (Vol~I \S shadow-tower; landscape\_census.tex line corresponding
to Virasoro).

\begin{definition}[Generic central charge for Virasoro;
\ClaimStatusDefinitional]
\label{def:vmp-generic-c}
The set of \emph{generic central charges} for $\Vir_c$ is
\[
 C^{\mathrm{gen}} \;=\; \mathbb{C} \setminus \bigl(\{0\} \cup \{-22/5\}
 \cup \{c_{p,q} : p, q \geq 2,\, \gcd(p,q) = 1\}\bigr),
\]
where $c_{p,q} = 1 - 6(p - q)^2 / (p q)$ are the minimal-model central
charges. At generic $c \in C^{\mathrm{gen}}$, the Shapovalov form on
each Virasoro Verma module is non-degenerate in every weight, and the
Zamolodchikov quasi-primary $\Lambda = {:}TT{:} -
\tfrac{3}{10}\,\partial^2 T$ has non-zero norm
$\langle \Lambda \mid \Lambda \rangle = c(5c+22)/10$; in particular
$c \neq 0$ and $5c + 22 \neq 0$.
\end{definition}

\begin{remark}[\label{rem:vmp-exclusions}Three removed loci]
The removal of $c = 0$ is forced by the $1/(r c)$ prefactor of the
master-equation recursion: at $c = 0$ the shadow tower is undefined.
The removal of $c = -22/5$ is forced by the Zamolodchikov quartic
norm: at $c = -22/5$, $\Lambda$ is null and $S_4$ diverges; this is
the Liouville barrier. Minimal-model points $c = c_{p,q}$ require
separate treatment (the Verma module has a proper submodule; the
shadow tower may vanish in certain weights by Feigin--Fuchs
cohomology, rather than being given by the generic formula); the
theorem below applies generically and the minimal-model points are
limits, studied in the Frontier part.
\end{remark}

\begin{theorem}[\label{thm:vmp-riccati-vir-recap}Riccati algebraicity
for Virasoro, recapitulation]
\ClaimStatusConditional
The weighted Riccati-metric shadow generating function for Virasoro on
the Koszul locus is
\[
 H^{\rm wt}_{\Vir}(t) \;=\; \sum_{r \geq 2} r\, \widehat S^{\rm wt}_r(\Vir_c)\, t^r
 \;=\; t^2\,\sqrt{Q(t)},
\]
where $Q(t) = 4\, \kapch(\Vir_c)^2 + 12\, \kapch(\Vir_c)\, S_3\, t
+ (9 S_3^2 + 16\, \kapch(\Vir_c)\, S_4)\, t^2 \in \mathbb{Q}(c)[t]$
is a quadratic polynomial in $t$ with coefficients in $\mathbb{Q}(c)$.
Explicitly, using $\kapch(\Vir_c) = c/2$, $S_3 = 2$,
$S_4 = 10/[c(5c+22)]$:
\[
 Q(t) \;=\; c^2 \;+\; 12\, c\, t
 \;+\; \left(36+\frac{80}{5c+22}\right)t^2
 \;=\; c^2 \;+\; 12 c\, t
 \;+\; \frac{180c+872}{5c+22}\,t^2.
\]
\end{theorem}

\begin{proof}
Theorem~\ref{thm:riccati-algebraicity} (higher\_genus\_modular\_koszul.tex)
is the conditional Riccati algebraicity input for a one-dimensional
primary slice of a chirally Koszul algebra in the standard landscape;
Virasoro fits this frame with the single primary $T(z)$, and the
three invariants $(\kapch(\Vir_c), S_3, S_4)$ are obtained from the
Virasoro OPE (Belavin--Polyakov--Zamolodchikov 1984) and from the
Zamolodchikov norm computation (Zamolodchikov 1986). No additional
content beyond the cited theorem and the family-specific values.
\end{proof}

\begin{definition}[\label{def:vmp-motivic-lift}Weighted motivic lift at
Virasoro]
In the notation of chapter~\ref{ch:motivic-shadow-tower}, the motivic
lift $\widehat S^{\rm wt,\mot}_r(\Vir_c) \in \MZV^{\mot}_r \otimes
\mathbb{Q}(c)$ is the element produced by applying the weighted
Riccati-metric projection after replacing the KZ associator
$\Phi_{\KZ}$ with the motivic associator $\Phi_{\KZ}^{\mot}$ throughout
the construction of $\Theta_{\Vir_c}$; the period map $\per$ sends
$\widehat S^{\rm wt,\mot}_r(\Vir_c)$ to
$\widehat S^{\rm wt}_r(\Vir_c) \in \mathbb{Q}(c)$.
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Virasoro motivic purity theorem}
\label{sec:vmp-main}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem}[\label{thm:virasoro-motivic-purity}Weighted Virasoro motivic
purity]
\ClaimStatusConditional
Let $c \in C^{\mathrm{gen}}$. For every $r \geq 2$, the weighted
Riccati-metric Virasoro shadow coefficient and its motivic lift satisfy
\[
 \widehat S^{\rm wt}_r(\Vir_c) \;\in\; \mathbb{Q}(c), \qquad
 \widehat S^{\rm wt,\mot}_r(\Vir_c)
 = \widehat S^{\rm wt}_r(\Vir_c) \otimes 1
 \;\in\; \mathbb{Q}(c) \;\subset\; \MZV^{\mot}_0 \otimes \mathbb{Q}(c).
\]
In particular no motivic multiple zeta value appears in
$\widehat S^{\rm wt,\mot}_r(\Vir_c)$: the $\mathbb{Q}$-linear component of
$\widehat S^{\rm wt,\mot}_r(\Vir_c)$ along any basis element
$\zet^{\mot}(n_1, \ldots, n_k)$ with $n_1 + \cdots + n_k \geq 2$ is
zero.
\end{theorem}

\begin{proof}
The proof has four steps.

\emph{Step 1: base rationality.} Virasoro's first three invariants
are rational:
$\kapch(\Vir_c) = c/2 \in \mathbb{Q}(c)$ (landscape\_census.tex);
$S_3 = 2 \in \mathbb{Q} \subset \mathbb{Q}(c)$ (three-point Ward
identity of $T(z)$, recording the single non-central channel of the
$T T$ OPE; computation in
Theorem~\ref{thm:virasoro-shadow-recurrence} proof);
$S_4 = 10/[c(5c+22)] \in \mathbb{Q}(c)$ (Shapovalov determinant at
weight $2$ and Zamolodchikov $\Lambda$-norm; Proposition
\ref{prop:s4-vir-mot}).

\emph{Step 2: Riccati transport preserves rationality.} By
Theorem~\ref{thm:vmp-riccati-vir-recap}, $H^{\rm wt}_{\Vir}(t) = t^2
\sqrt{Q(t)}$ with $Q(t) \in \mathbb{Q}(c)[t]$ a quadratic polynomial.
The formal Taylor expansion of $\sqrt{Q(t)}$ around $t = 0$ is
\[
 \sqrt{Q(t)} \;=\; \sqrt{Q(0)}\, \sum_{n \geq 0} \binom{1/2}{n}\,
 \left(\frac{Q(t) - Q(0)}{Q(0)}\right)^n,
\]
with $\binom{1/2}{n} \in \mathbb{Q}$ the central binomial series
coefficient and $Q(0) = 4\, \kapch(\Vir_c)^2 = c^2$. Since $c \neq 0$
on $C^{\mathrm{gen}}$, choose the formal branch
$\sqrt{Q(0)}=\sqrt{c^2}=c$, the one compatible with
$H^{\rm wt}_{\Vir}(t) = c\, t^2 + O(t^3)$; note
$H^{\rm wt}_{\Vir}$ is defined up to sign on
$\sqrt{Q(0)}$, and the positive branch is fixed by the normalisation
$2S_2 = c$. The Taylor expansion is therefore a
$\mathbb{Q}(c)$-linear combination of products of the coefficients of
$Q(t)$, each of which lies in $\mathbb{Q}(c)$; hence every coefficient
of $H^{\rm wt}_{\Vir}(t)$ lies in $\mathbb{Q}(c)$.

Explicitly, for $r \geq 2$,
\[
 r\, \widehat S^{\rm wt}_r(\Vir_c) \;=\; [t^r]\, H^{\rm wt}_{\Vir}(t)
 \;=\; [t^{r-2}]\,\sqrt{Q(t)}
 \;\in\; \mathbb{Q}(c),
\]
and division by the non-zero rational integer $r$ keeps the result in
$\mathbb{Q}(c)$.

\emph{Step 3: motivic lift is trivial.} The weighted motivic lift
$\widehat S^{\rm wt,\mot}_r(\Vir_c)$ is defined in
Definition~\ref{def:vmp-motivic-lift} as the image of
$\widehat S^{\rm wt}_r(\Vir_c)$
under the inclusion $\mathbb{Q}(c) \hookrightarrow
\MZV^{\mot} \otimes \mathbb{Q}(c)$ induced by the motivic associator
construction of
Theorem~\ref{thm:shadow-tower-motivic-lift}. If
$\widehat S^{\rm wt}_r(\Vir_c)$ is an
element of the rational subfield $\mathbb{Q}(c) \subset \MZV^{\mot}_0
\otimes \mathbb{Q}(c) \subset \MZV^{\mot} \otimes \mathbb{Q}(c)$, then
$\widehat S^{\rm wt,\mot}_r(\Vir_c) = \widehat S^{\rm wt}_r(\Vir_c)
\otimes 1$, and its $\mathbb{Q}$-linear
expansion in the Brown basis of $\MZV^{\mot}$ has a single non-zero
coefficient, namely along the unit $1 \in \MZV^{\mot}_0$.

\emph{Step 4: period-map consistency.} Applying
$\per \colon \MZV^{\mot} \to \mathbb{R}$ to
$\widehat S^{\rm wt,\mot}_r(\Vir_c)
=\widehat S^{\rm wt}_r(\Vir_c)\otimes1$ recovers
$\widehat S^{\rm wt}_r(\Vir_c)$ tautologically (rational numbers are fixed by the
period map), consistent with
Theorem~\ref{thm:shadow-tower-motivic-lift} Step~4. Since no
$\zet^{\mot}(n_1, \ldots, n_k)$ term appears with $n_1 + \cdots + n_k
\geq 2$, the motivic coaction has no positive-weight component on
the weighted Virasoro shadow tower.
\end{proof}

\begin{remark}[\label{rem:vmp-convergence-of-sqrt}Formal vs.\
analytic square root]
The Taylor expansion of $\sqrt{Q(t)}$ around $t = 0$ used in Step~2
is a \emph{formal} power-series identity in $\mathbb{Q}(c)[[t]]$; it
does not require convergence or a branch cut (we operate in the formal
power-series ring, not in a punctured disk). The discriminant
$\Delta(Q)=144c^2-4c^2(180c+872)/(5c+22)
=-320c^2/(5c+22)$ governs \emph{analytic} algebraicity (finite radius of
convergence versus entire function), which is logically separate from
formal rationality.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Denominator structure}
\label{sec:vmp-denominator}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The closed-form computations at $r = 4, 5, 6, 7, 8$
(chapter~\ref{ch:shadow-tower-higher-coefficients}) exhibit a uniform
denominator structure. The following proposition gives the precise
bound.

\begin{proposition}[\label{prop:denominator-structure}Denominator of
$\widehat S^{\rm wt}_r(\Vir_c)$]
\ClaimStatusProvedHere
For every $r \geq 2$, the reduced-form denominator of
$\widehat S^{\rm wt}_r(\Vir_c) \in \mathbb{Q}(c)$ divides
\[
 D_r \;=\; c^{\max(0, r-3)} \;\cdot\; (5c + 22)^{\lfloor (r-2)/2 \rfloor}.
\]
Explicitly: $D_2 = 1$, $D_3 = 1$, $D_4 = c(5c+22)$,
$D_5 = c^2(5c+22)$, $D_6 = c^3(5c+22)^2$, $D_7 = c^4(5c+22)^2$,
$D_8 = c^5(5c+22)^3$. In particular, the only irreducible factors of
denominators across the Virasoro shadow tower are $c$ and $(5c+22)$;
no new irreducible factor (such as $7c + 68$, $c + 1$, or $c + 2$)
enters at any weight.
\end{proposition}

\begin{proof}
The base cases $r = 2, 3$ are immediate:
$\widehat S^{\rm wt}_2(\Vir_c) = c/2$ has
denominator $1$ (we absorb the $2$ into the numerator); $S_3 = 2$ has
denominator $1$. The case $r = 4$ is
Proposition~\ref{prop:s4-vir-mot} with denominator $c(5c+22)$; the
case $r = 5$ is Proposition~\ref{prop:s5-vir-mot} with denominator
$c^2(5c+22)$. The weighted square-root metric coefficient at $r=6$ is
$\widehat S^{\rm wt}_6 = 80(45c+193)/[3 c^3 (5c+22)^2]$, while the
manuscript shadow coefficient is not used in this proposition. The remaining weighted
closed forms through $r=8$ are
$\widehat S^{\rm wt}_7 = -2880(15c + 61)/[7 c^4 (5c+22)^2]$,
$\widehat S^{\rm wt}_8 = 80(2025 c^2 + 16470 c + 33314)/[c^5(5c+22)^3]$
of Theorems~\ref{thm:s6-virasoro-closed-form},
\ref{thm:s7-virasoro-closed-form}, \ref{thm:s8-virasoro-closed-form}.
All eight cases satisfy the stated bound directly.

For the induction step $r \geq 6$, apply the master-equation
recurrence
\[
 \widehat S^{\rm wt}_r(\Vir_c) \;=\; -\,\frac{1}{r c}
 \sum_{\substack{j + k = r + 2 \\ 3 \leq j \leq k < r}}
 \varepsilon(j, k)\, j k\, \widehat S^{\rm wt}_j(\Vir_c)\,
 \widehat S^{\rm wt}_k(\Vir_c)
\]
(Theorem~\ref{thm:virasoro-shadow-recurrence}). Each product
$\widehat S^{\rm wt}_j(\Vir_c)\,\widehat S^{\rm wt}_k(\Vir_c)$ has denominator dividing $D_j \cdot D_k$
by the inductive hypothesis. The prefactor $1/(rc)$ contributes one
additional factor of $c$ (absorbing into $c^{r-3}$ since the highest
exponent $r - 3$ in $D_r$ exceeds the exponents $j - 3 + k - 3 = r -
4$ by $1$). The power of $(5c + 22)$ in the denominator is bounded by
$\max_{(j,k)}\lfloor (j-2)/2 \rfloor + \lfloor (k-2)/2 \rfloor$ over
admissible pairs. In both parities this sum is at most
$\lfloor (r - 2)/2 \rfloor$, by direct arithmetic:
\begin{itemize}
\item Even $r = 2m$: every admissible pair satisfies
$\lfloor (j-2)/2 \rfloor+\lfloor (k-2)/2 \rfloor\leq m-1
=\lfloor(r-2)/2\rfloor$.
\item Odd $r = 2m + 1$: every admissible pair satisfies
$\lfloor (j-2)/2 \rfloor+\lfloor (k-2)/2 \rfloor\leq m-1
=\lfloor(r-2)/2\rfloor$.
\end{itemize}
Adding the fresh $1/(rc)$ contributes no new irreducible factor (the
integer $r$ reduces in $\mathbb{Q}(c)$ to a rational scalar). Hence
$D_r$ absorbs all denominators appearing in the inductive product, and
the bound propagates.

No new irreducible factor enters at any weight because the recurrence
itself introduces only the factor $c$ (via $1/(rc)$); every other
denominator contribution inherits from $D_j \cdot D_k$, and the
bracket structure of Virasoro on a one-dimensional primary slice has
exactly one non-central OPE channel (the $2 T(w)/(z-w)^2$ descendant
exchange), whose iterated re-contraction against $\Lambda$-channels
produces only $(5c + 22)$-factors. No admissible pair $(j, k)$ in the
recurrence produces a $\mathbb{Q}$-irreducible factor of $c$ other
than $c$ itself, and no admissible pair produces a
$\mathbb{Q}(c)$-irreducible factor of $(5c + 22)$ other than
$(5c + 22)$ itself.
\end{proof}

\begin{remark}[\label{rem:vmp-growth}Slow polynomial growth]
The denominator $D_r$ grows as $c^{r-3}$ in the first generator and
$(5c + 22)^{\lfloor (r-2)/2 \rfloor}$ in the second; the total
$c$-degree of the denominator is $r - 3 + \lfloor (r-2)/2 \rfloor \leq
3r/2$, linear in $r$. By contrast, the numerator degree in $c$ is
bounded by Proposition~\ref{prop:s8-c-degree-bound} at $r \leq 8$ and
by a parallel induction at general $r$; the ratio
$\deg_c\mathrm{num}/\deg_c\mathrm{denom}$ has limit $1/2$, which is
precisely the scalar rank-$1$ behaviour for a single-primary chiral
algebra.
\end{remark}

\begin{remark}[\label{rem:vmp-c1-excluded}$c = 1$ specialisation
remains rational]
At $c = 1$ (free-boson point), $D_r$ specialises to
$27^{\lfloor (r-2)/2 \rfloor}$: $D_6 = 3^6 = 729$,
$D_7 = 27^2 = 729$, $D_8 = 27^3 = 19683$. The appearance of
$3^9 = 19683$ in the denominator of
$\widehat S^{\rm wt}_8(\Vir_1) = 4144720/19683$
(chapter~\ref{ch:shadow-tower-higher-coefficients}) matches the Vol
III $m_8 = 4144720/19683$ specialisation and confirms that the
denominator is a pure power of $27 = (5 \cdot 1 + 22)$, with no
extraneous prime. This is the prime-power denominator structure of
the Vol~III $m_8 = 4144720/19683$ specialization: with
$19683 = 3^9$ corresponds to Virasoro at $c = 1$, where
$(5c + 22) = 27 = 3^3$, and the denominator of $S_8(\Vir_1) = D_8 =
27^3 = 3^9$ matches exactly.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Rationality of the Riccati shadow-transport operator}
\label{sec:vmp-transport}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem}[\label{thm:virasoro-riccati-transport-rationality}
Rationality of the weighted Riccati transport operator on Virasoro]
\ClaimStatusConditional
Let $\mathcal{T}^{\rm wt}_{\Vir} \colon \mathbb{Q}(c)^{\oplus 3} \to
\mathbb{Q}(c)[[t]]$ be the \emph{weighted Riccati shadow-transport operator} on
Virasoro:
\[
 \mathcal{T}^{\rm wt}_{\Vir}(\kapch, S_3, S_4)
 \;=\; t^2\, \sqrt{4\, \kapch^2 + 12\, \kapch\, S_3\, t
 + (9 S_3^2 + 16\, \kapch\, S_4)\, t^2}.
\]
Then:
\begin{enumerate}[(i)]
\item $\mathcal{T}^{\rm wt}_{\Vir}$ sends rational triples to formal power
series in $\mathbb{Q}(c)[[t]]$; in particular it preserves the
$\mathbb{Q}(c)$-subring of the formal power-series ring.
\item Extracting the $t^r$-coefficient and dividing by $r$ yields
$\widehat S^{\rm wt}_r(\Vir_c) \in \mathbb{Q}(c)$ for every $r \geq 2$.
\item Composition with the motivic lift map
$\iota^{\mot} \colon \mathbb{Q}(c) \hookrightarrow \MZV^{\mot}
\otimes \mathbb{Q}(c)$ factors through the rational sub-comodule:
$\iota^{\mot} \circ [t^r]\, \mathcal{T}^{\rm wt}_{\Vir}
=\widehat S^{\rm wt,\mot}_r(\Vir_c)
\in \MZV^{\mot}_0 \otimes \mathbb{Q}(c) = \mathbb{Q}(c)$.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{(i)} The argument of the square root is a quadratic polynomial
in $t$ with coefficients in $\mathbb{Q}(c)$. Formal square roots of
power series $P(t) = P(0) + t\, P'(0) + \ldots$ with non-zero constant
term $P(0) \neq 0$ in $\mathbb{Q}(c)$ are defined in
$\mathbb{Q}(c)[[t]]$ via the binomial series (after possibly extending
by $\sqrt{P(0)}$). For
$P(t) = Q(t) = c^2 + 12 c\, t + \ldots$ with $c \neq 0$, we have
$\sqrt{Q(0)} = c \in \mathbb{Q}(c)$, and the extension is trivial:
$\sqrt{Q(t)} = c\, \sqrt{1 + (Q(t) - c^2)/c^2}$ expands via
$\sum_{n \geq 0} \binom{1/2}{n}\, ((Q(t) - c^2)/c^2)^n$, which is a
formal power series in $\mathbb{Q}(c)[[t]]$ because
$\binom{1/2}{n} \in \mathbb{Q}$ and $(Q(t) - c^2)/c^2$ has no constant
term. Multiplying by the $t^2$ prefactor keeps the result in
$\mathbb{Q}(c)[[t]]$.

\emph{(ii)} By Theorem~\ref{thm:vmp-riccati-vir-recap},
$\mathcal{T}^{\rm wt}_{\Vir}(\kapch(\Vir_c), 2, 10/[c(5c+22)])
= H^{\rm wt}_{\Vir}(t) =
\sum_{r \geq 2} r\, \widehat S^{\rm wt}_r(\Vir_c)\, t^r$; extracting the $t^r$-
coefficient and dividing by $r \in \mathbb{Q}^{\times}$ gives
$\widehat S^{\rm wt}_r(\Vir_c) \in \mathbb{Q}(c)$.

\emph{(iii)} The motivic lift map $\iota^{\mot}$ is by construction
the composition of the inclusion $\mathbb{Q}(c) \hookrightarrow
\MZV^{\mot}_0 \otimes \mathbb{Q}(c)$ (Brown 2012 Thm.\ 1.1:
$\MZV^{\mot}_0 = \mathbb{Q}$) with the identity on $\mathbb{Q}(c)$-
coefficients. Therefore
$\iota^{\mot}(\widehat S^{\rm wt}_r(\Vir_c))
=\widehat S^{\rm wt}_r(\Vir_c)\otimes 1$ lies in the weight-$0$
graded component, in agreement with
the Theorem~\ref{thm:virasoro-motivic-purity} conclusion.
\end{proof}

\begin{remark}[\label{rem:vmp-binary-bracket-closure}Binary-bracket
closure is the mechanism]
The deep reason Virasoro's Riccati transport preserves
$\mathbb{Q}(c)$-rationality is \emph{binary-bracket closure}: the
Virasoro OPE $T(z) T(w)$ is a quadratic polynomial in
$1/(z - w)$ with rational residues (central term $c/2$, stress
exchange $2 T(w)$, descendant $\partial T(w)$), and no higher primary
enters. The shadow tower's recursion combines only binary products
$S_j S_k$ with rational prefactors $\varepsilon(j, k)\, j k / (r c)$;
no triple or higher iterated bracket appears. For algebras with
ternary or higher brackets (e.g.\ $W_3$, which has a spin-$3$ primary
$W(z)$ with $W W$ OPE producing a weight-$3$ Arnold period), the
Riccati transport acquires additional terms and rationality may be
broken; this is the content of
Section~\ref{sec:vmp-w-algebra-comparison}.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{No MZV contribution: motivic coaction is trivial}
\label{sec:vmp-no-mzv}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{corollary}[\label{cor:virasoro-no-mzv-contribution}Motivic
coaction on the weighted Virasoro shadow tower is trivial]
\ClaimStatusConditional
For every $r \geq 2$ and every $c \in C^{\mathrm{gen}}$, the motivic
coaction $\Delta^{\mot}$ on $\widehat S^{\rm wt,\mot}_r(\Vir_c)$ is trivial:
\[
 \Delta^{\mot}\bigl(\widehat S^{\rm wt,\mot}_r(\Vir_c)\bigr)
 \;=\; 1 \otimes \widehat S^{\rm wt,\mot}_r(\Vir_c)
 \;+\; \widehat S^{\rm wt,\mot}_r(\Vir_c) \otimes 1,
\]
with no $\zet^{\mot}(2n+1)$-term for any $n \geq 1$.
\end{corollary}

\begin{proof}
By Theorem~\ref{thm:virasoro-motivic-purity},
$\widehat S^{\rm wt,\mot}_r(\Vir_c) \in
\MZV^{\mot}_0 \otimes \mathbb{Q}(c)$. The coaction
$\Delta^{\mot}$ acts as the identity on weight-$0$ elements of
$\MZV^{\mot}$ (Brown 2012 Prop.\ 2.1: weight-$0$ is the group-like
component of the motivic Galois Hopf algebra); explicitly, for
$q \in \mathbb{Q} \subset \MZV^{\mot}_0$,
$\Delta^{\mot}(q) = q \otimes 1 = 1 \otimes q$. Hence the coaction on
$\widehat S^{\rm wt,\mot}_r(\Vir_c)
=\widehat S^{\rm wt}_r(\Vir_c) \otimes 1$ is
$1 \otimes \widehat S^{\rm wt,\mot}_r(\Vir_c)
+ \widehat S^{\rm wt,\mot}_r(\Vir_c) \otimes 1$
(primitive), and no $\zet^{\mot}(2n+1)$-generator of the Hopf algebra
appears because every such generator has weight $\geq 3 > 0$.

In particular, at $r \leq 5$ (where
Theorem~\ref{thm:grt-motivic-coaction} would a priori permit a
$\sigma_{r-j}^W \otimes S_j^{\mot}$ term for $3 \leq r - j \leq r$),
the coaction evaluates to trivial on Virasoro: the Willwacher
cocycle $\sigma^W$ acts on the \emph{universal} associator
$\Phi_{\KZ}^{\mot}$ but the \emph{averaged projection} onto Virasoro's
scalar shadow kills every non-rational component. This is consistent
with the direct computation
$\Delta^{\mot}(S_2^{\mot}(\Vir_c)) = \Delta^{\mot}(c/2) = c/2 \otimes 1
= 1 \otimes c/2$ (rational scalars are primitive).
\end{proof}

\begin{remark}[\label{rem:vmp-grt-action-trivial-on-vir}$\mathrm{GRT}$
acts trivially on the weighted Virasoro shadow tower]
Theorem~\ref{thm:grt-motivic-coaction} asserts that
$\GRT(\mathbb{Q})$ coacts on the motivic shadow tower. For Virasoro
specifically, Corollary~\ref{cor:virasoro-no-mzv-contribution} shows
the coaction restricts to the trivial action: $\GRT(\mathbb{Q})$-
torsor elements acting on the weighted Virasoro face of the shadow
tower leave every $\widehat S^{\rm wt,\mot}_r(\Vir_c)$ invariant.
This is the motivic-side
expression of Virasoro's single-generator rigidity: $\GRT$ acts on
the multi-generator data (associator), but Virasoro's scalar shadow
is insensitive to the multi-generator content because it lives in the
rational subfield $\mathbb{Q}(c)$.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparison with $W_3$ and finite-lane propagation}
\label{sec:vmp-w-algebra-comparison}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{remark}[\label{rem:vir-vs-w3-contrast}Where $W_3$ can acquire a
period]
Virasoro has one generator ($T(z)$ of conformal weight $2$); its OPE
$T(z) T(w)$ has three channels (central $c/2$, stress exchange
$2 T(w)$, descendant $\partial T(w)$), all rational in $c$. The
shadow-tower Riccati transport closes on the three invariants
$(\kapch(\Vir_c), S_3, S_4)$, none of which involves a weight-$3$
Arnold period.

Principal $W_3 = W_3(sl_3)$ has two generators ($T(z)$ of weight $2$
and $W(z)$ of weight $3$); the $W W$ OPE contains higher collision
channels absent from the Virasoro line. These channels are possible
sources of Arnold/KZ periods. They become actual motivic contributions
only after the corresponding period pairing is computed and shown to
survive ordered-to-symmetric averaging
(Proposition~\ref{prop:s6-w3-mot}).

In short: weighted Virasoro motivic purity is proved for every weight because
the stress tensor is Virasoro's only primary and its OPE is
$\mathbb{Q}(c)$-rational. The $W_3$ spin-$3$ primary marks the first
period boundary; it does not by itself prove non-purity.
\end{remark}

\begin{remark}[\label{rem:vmp-wn-propagation-bound}Possible period
window for $\Walg_N$]
Generalising Remark~\ref{rem:vir-vs-w3-contrast}: principal
$\Walg_N = \Walg_N(sl_N)$ has generators of conformal weights
$\{2, 3, \ldots, N\}$. A spin-$k$ primary with $k \geq 3$ can
contribute an Arnold period only if its ordered period pairing survives
the symmetric shadow projection. Consequently the weighted Virasoro
rationality theorem extends automatically only to the stress-tensor projection. For
non-stress-tensor generator lines, the expected period boundary is a
computation, not a theorem. For $N = 3$,
Proposition~\ref{prop:s6-w3-mot} identifies the first possible
boundary; it does not assert a non-zero motivic coefficient.
\end{remark}

\begin{corollary}[\label{cor:vir-purity-propagates-to-dress-reduced}
Motivic purity in the Drinfeld--Sokolov reduction chain]
\ClaimStatusConditional
Let $\Walg$ be a principal $\Walg$-algebra obtained as a
Drinfeld--Sokolov reduction of affine $\hat{sl}_N$. The DS ghost
cohomology is rational at the chain-level by Arakawa 2007 and
Kac--Roan--Wakimoto 2003; hence the shadow-tower projection of
$\Walg$ onto its Virasoro sub-algebra (the stress-tensor component)
inherits weighted rationality, and the Virasoro scalar projection of
$\widehat S^{\rm wt,\mot}_r(\Walg)$ equals
$\widehat S^{\rm wt,\mot}_r(\Vir_{c(\Walg)}) \in
\mathbb{Q}(c(\Walg))$ for every $r \geq 2$.

Non-stress-tensor contributions to $S_r^{\mot}(\Walg)$ (arising from
spin-$\geq 3$ primaries) require their own finite-lane or period-pairing
calculation.
\end{corollary}

\begin{proof}
DS reduction $H_{\mathrm{DS}}^0(\hat{sl}_N, V) = \Walg$ is exact at
the chain level on principal nilpotents (Arakawa 2007 Thm.\ 4.3). The
reduction intertwines the Virasoro sub-algebra of $\hat{sl}_N$ (the
Sugawara stress tensor) with the Virasoro sub-algebra of $\Walg$
(the leading $T(z)$ of the $\Walg$-stress-tensor series), with a
rational shift of central charge $c(\Walg) = c(\hat{sl}_N) - 12
|\rho|^2 (k + h^\vee)^{-1}$ (Kac--Roan--Wakimoto 2003; landscape\_
census.tex, $\Walg$ row for $sl_N$). Restricting the shadow tower
of $\Walg$ to the Virasoro sub-algebra gives the weighted Virasoro
coefficient $\widehat S^{\rm wt,\mot}_r(\Vir_{c(\Walg)})$, and by
Theorem~\ref{thm:virasoro-motivic-purity} this weighted sub-shadow
tower is rational in $c(\Walg)$. The full $\Walg$-shadow tower contains
additional non-Virasoro components from spin-$\geq 3$ primaries. Their
motivic weight is not decided by the Virasoro projection.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Epilogue}
\label{sec:vmp-epilogue}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The weighted Virasoro motivic purity theorem
(Theorem~\ref{thm:virasoro-motivic-purity}) completes the arithmetic
characterisation of the weighted Virasoro shadow tower. Three consequences
close loose ends left open in chapter~\ref{ch:motivic-shadow-tower}.

First, the weighted extrapolation from $r \leq 5$ to all $r \geq 2$ is
grounded in the Riccati algebraicity of $H^{\rm wt}_{\Vir}(t)$, not in
a weight-by-weight cohomological vanishing.
The Feigin--Fuchs vanishing argument of
Remark~\ref{rem:w3-first-zeta3} is a separate fact about Virasoro
module cohomology; it is not used in the proof above.

Second, the $\mathrm{GRT}$-torsor action on the motivic shadow tower
(Theorem~\ref{thm:grt-motivic-coaction}) restricts to the trivial
action on Virasoro (Remark~\ref{rem:vmp-grt-action-trivial-on-vir}).
This is a family-specific restriction of the universal coaction.
Higher families ($W_N$, $N \geq 3$) may carry non-trivial
$\mathrm{GRT}$-action from spin-$\geq 3$ period pairings, but this must
be checked on the chosen ordered-to-symmetric shadow lane. Virasoro is
the \emph{$\mathrm{GRT}$-trivial} stratum.

Third, the denominator bound
(Proposition~\ref{prop:denominator-structure}) gives a concrete
arithmetic finiteness for the Virasoro shadow tower: the full tower
embeds in the two-generator multiplicative monoid $\langle c,\,
5c + 22 \rangle$ inside $\mathbb{Q}(c)^{\times}$. No prime factor of
the shadow tower denominator escapes this monoid; in particular, at
$c = 1$, every $S_r(\Vir_1) \in \mathbb{Z}[1/27]$ is a $27$-adic
rational, explaining the Vol III specialisation
$m_8 = 4144720/19683 = 4144720/27^3$.

The frontier is the motivic classification of $W_N$ shadow towers for
$N \geq 4$: the possible period boundary of
Remark~\ref{rem:vmp-wn-propagation-bound} must be tested by explicit
Arnold/KZ pairings and by the ordered-to-symmetric averaging map. That
programme lies outside the scope of the Virasoro chapter.
