\documentclass[11pt,reqno]{amsart}

% ================================================================
%  Packages
% ================================================================
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathrsfs}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{booktabs}
\usepackage{array}
\usepackage{microtype}
\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks=true,linkcolor=blue!60!black,citecolor=green!40!black,urlcolor=blue!60!black]{hyperref}
\usepackage[all]{xy}

% ================================================================
%  Theorem environments
% ================================================================
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{construction}[theorem]{Construction}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% ================================================================
%  Macros
% ================================================================
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\barB}{\bar{B}}
\newcommand{\barC}{\overline{C}}
\newcommand{\Defcyc}{\mathrm{Def}_{\mathrm{cyc}}}
\newcommand{\Ran}{\mathrm{Ran}}
\newcommand{\MC}{\mathrm{MC}}
\newcommand{\Sym}{\mathrm{Sym}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\Ext}{\mathrm{Ext}}
\newcommand{\Res}{\mathrm{Res}}
\newcommand{\Aut}{\mathrm{Aut}}
\newcommand{\FM}{\overline{C}}
\newcommand{\fg}{\mathfrak{g}}
\newcommand{\fh}{\mathfrak{h}}
\newcommand{\gmod}{\mathfrak{g}^{\mathrm{mod}}_\cA}
\newcommand{\Sh}{\mathrm{Sh}}
\newcommand{\OPE}{\mathrm{OPE}}
\newcommand{\Vir}{\mathrm{Vir}}
\newcommand{\Ahat}{\widehat{A}}
\newcommand{\cW}{\mathcal{W}}

\DeclareMathOperator{\gr}{gr}
\DeclareMathOperator{\rk}{rk}
\DeclareMathOperator{\depth}{depth}

\numberwithin{equation}{section}

% ================================================================
\begin{document}

\title[Modular Koszul Duality and the Shadow Tower]
{Modular Koszul Duality and the Shadow Tower:\\
Algebraicity, Depth Classification,\\
and the Gravitational Coproduct}

\author{Raeez Lorgat}
\address{Department of Mathematics, Harvard University, Cambridge, MA 02138}
\email{raeez@math.harvard.edu}

\date{\today}

\begin{abstract}
Let $\cA$ be a chirally Koszul vertex algebra on a smooth projective
curve~$X$, with modular characteristic $\kappa = \kappa(\cA)$, cubic
shadow $\alpha$, and quartic shadow~$S_4$.  The bar construction
$\barB^{\mathrm{ch}}(\cA)$ defines a Maurer--Cartan element
$\Theta_\cA$ in the modular convolution dg Lie algebra, whose
finite-order projections $\Theta_\cA^{\le r}$ form the
\emph{shadow Postnikov tower}.

We prove six results.
First, on each one-dimensional primary line~$L$ in the
cyclic deformation complex, the weighted shadow generating function
$H(t) = \sum_{r \ge 2} r\, S_r\, t^r$ satisfies the algebraic
relation $H(t)^2 = t^4 Q(t)$, where
$Q(t) = 4\kappa^2 + 12\kappa\alpha\, t
+ (9\alpha^2 + 16\kappa S_4)\, t^2$
is the \emph{shadow metric}: the tower is algebraic of degree~$2$
along~$L$, and every coefficient $S_r$ for $r \ge 5$ is determined
by the three seed invariants $(\kappa, \alpha, S_4)$ of~$L$.
Second, the \emph{critical discriminant} $\Delta = 8\kappa S_4$
partitions the standard Lie-theoretic landscape into four depth
classes: Gaussian ($r_{\max} = 2$), Lie ($r_{\max} = 3$), contact
($r_{\max} = 4$), and mixed ($r_{\max} = \infty$), with $\Delta = 0$
on the primary line forcing finite depth and $\Delta \ne 0$
forcing infinite depth.
Third, we compute the genus-$2$ free energy
$F_2 = \kappa \cdot 7/5760$ for single-generator algebras
by an explicit stable-graph sum, carry out the first
multi-channel computation for~$\mathcal{W}_3$ (exhibiting
a cross-channel correction whose cancellation is equivalent
to multi-generator universality at genus~$2$), and derive
the planted-forest correction
$\delta_{\mathrm{pf}}^{(2,0)} = S_3(10 S_3 - \kappa)/48$.
Fourth, we prove that the gravitational coproduct, obtained by
homological perturbation transfer through BRST reduction from
$\widehat{\mathfrak{sl}}_N$ to $\cW_N$, is strictly primitive
at all arities for every principal Drinfeld--Sokolov reduction:
gravity does not produce particles, only braids.
Fifth, for class~$\mathbf{M}$ algebras at rational central
charge, the shadow metric~$Q_L$ defines an Epstein zeta function
$\varepsilon_{Q_L}(s) = \sum'_{(m,n)} Q_L(m,n)^{-s}$
with a functional equation $s \leftrightarrow 1-s$, and the
discriminant of~$Q_L$ determines an imaginary quadratic
\emph{shadow field}
$K_L = \mathbb{Q}(\sqrt{\operatorname{disc}(Q_L)})$
through which the Epstein zeta factors via a
Dirichlet $L$-function: the chain
$\cA \to Q_L \to K_L \to L(s, \chi_d)$ produces
arithmetic from OPE data.
Sixth, we verify the genus-$2$ prediction $F_2(V_{E_8}) = 7/720$
against the Siegel--Weil formula and direct lattice enumeration:
the bar complex knows that each of the~$240$ $E_8$ roots has
exactly~$126$ orthogonal partners.
\end{abstract}

\subjclass[2020]{17B69, 14H10, 18M70, 81T40}

\keywords{Chiral algebras, bar construction, Koszul duality,
moduli of curves, vertex algebras, Maurer--Cartan,
W-algebras, gravitational coproduct, Epstein zeta function,
shadow field}

\maketitle

% ================================================================
%  1. INTRODUCTION
% ================================================================

\section{Introduction}\label{sec:intro}

\subsection{The question}

Classical Koszul duality is a phenomenon of graded algebras
over a point.  A quadratic algebra~$A$ determines a dual
coalgebra~$A^!$; the bar construction $B(A)$ mediates between
them; and the Koszul property (bar cohomology concentrated in
bar degree~$1$) is equivalent to the existence of a linear
resolution.  The theory is the subject of Priddy~\cite{Priddy70},
Beilinson--Ginzburg--Soergel~\cite{BGS96}, and
Loday--Vallette~\cite{LV12}.

On an algebraic curve~$X$, the generators of the algebra become
sections of a $\mathcal{D}_X$-module, the quadratic relations
become operator product expansions with meromorphic singularities,
and the bar differential becomes an integral transform whose
kernel is the logarithmic $1$-form
$\eta_{ij} = d\log(z_i - z_j)$ on the Fulton--MacPherson
compactification $\FM_n(X)$ of the configuration space.  The
resulting object, the \emph{chiral bar complex}
$\barB^{\mathrm{ch}}(\cA)$, is a factorization coalgebra on the
Ran space $\Ran(X)$ \cite{BD04, FG12, CG17}.

At genus~$0$, the classical theory embeds faithfully.  At
genus~$g \ge 1$, the topology of the curve forces genuinely new
structure: the bar differential acquires curvature
$d_{\mathrm{fib}}^2 = \kappa(\cA) \cdot \omega_g$, where
$\omega_g = c_1(\mathbb{E})$ is the Hodge class on
$\overline{\cM}_g$ and the scalar
$\kappa(\cA) \in \mathbb{Q}(c)$ is an intrinsic invariant of
the algebra called the \emph{modular characteristic}.  This
curvature has no analogue in the classical setting; its geometric
origin is the nontriviality of the Hodge bundle over
$\overline{\cM}_g$.

The present paper addresses a single question: \emph{what
invariants does the chiral bar construction produce, beyond the
modular characteristic?}

\subsection{The answer: the shadow obstruction tower}

The bar complex on a curve of genus~$g$ with $n$ marked points
defines a pronilpotent dg Lie algebra $\gmod$ (the modular
convolution algebra), whose differential encodes graph sums over
stable curves.  The boundary-of-boundary relation
$\partial^2 = 0$ on $\overline{\cM}_{g,n}$ implies $D^2 = 0$ on
$\gmod$, and the element $\Theta_\cA := D_\cA - d_0$ is
therefore a Maurer--Cartan element:
$D \Theta_\cA + \frac{1}{2}[\Theta_\cA, \Theta_\cA] = 0$.

The MC element $\Theta_\cA$ encodes the full genus expansion.
Its finite-order projections $\Theta_\cA^{\le r}$, obtained by
truncating the arity filtration at level~$r$, form the
\emph{shadow Postnikov tower}.  At arity~$2$, the tower
produces the modular characteristic~$\kappa$.  At arity~$3$,
a cubic shadow~$\alpha$ (the structure constant of the transferred
$L_\infty$ bracket $\ell_3$).  At arity~$4$, a quartic
shadow~$S_4$ (the first genuinely nonlinear invariant, measuring
the contact term in the four-point collision residue).

The obstruction to truncating $\Theta_\cA$ at finite arity is
measured by classes
$o_{r+1}(\cA) \in H^2(\cA^{\mathrm{sh}}_{r+1,0})$ in the
shadow algebra $\cA^{\mathrm{sh}} := H_\bullet(\Defcyc^{\mathrm{mod}}(\cA))$.
When $o_{r+1} = 0$, the tower stops; when $o_{r+1} \ne 0$, the
next shadow coefficient $S_{r+1}$ is forced.  The question is
how far this process continues and what controls it.

\subsection{Five movements}

The paper develops in five movements.  First, the universal
MC element $\Theta_\cA$ and its shadow obstruction tower as the primary
object.  Second, the algebraicity theorem: the tower is a
square root, $H = t^2\sqrt{Q_L}$, controlled by a quadratic
form in the arity parameter.  Third, the four-class partition
G/L/C/M determined by the critical discriminant $\Delta$.
Fourth, the explicit computations: genus-$2$ graph sums,
the $E_8$ decisive test, gravitational coproduct primitivity.
Fifth, the arithmetic frontier: the Epstein zeta function of
the shadow metric, the shadow field, and the descent fan from
$\Theta_\cA$ to three mathematical worlds.

\subsection{The shadow metric and algebraicity}

The first main result (Theorem~\ref{thm:main}, parts (i)--(ii))
is that the shadow obstruction tower is controlled by a single quadratic
polynomial.

Restrict to a one-dimensional primary slice~$L$ of the
cyclic deformation complex (the space spanned by a single primary
field~$\eta$ of definite conformal weight).  On~$L$, the
MC recursion reduces to a scalar recursion for the shadow
coefficients $S_r$, and the weighted generating function
$H(t) = \sum_{r \ge 2} r\,S_r\,t^r$ satisfies the algebraic
relation
\begin{equation}\label{eq:intro-algebraic}
  H(t)^2 \;=\; t^4\,Q(t),
\end{equation}
where the \emph{shadow metric}
\begin{equation}\label{eq:intro-shadow-metric}
  Q(t)
  \;=\;
  4\kappa^2 + 12\kappa\alpha\,t
  + (9\alpha^2 + 16\kappa S_4)\,t^2
\end{equation}
is a quadratic polynomial whose coefficients are determined by the
three seed invariants $(\kappa, \alpha, S_4)$ of the algebra.
The generating function is therefore algebraic of degree~$2$:
$H(t) = t^2 \sqrt{Q(t)}$.  Every shadow coefficient $S_r$
for $r \ge 5$ is a rational function of $(\kappa, \alpha, S_4)$,
computable from the binomial expansion of~$\sqrt{Q}$.

The proof converts the Maurer--Cartan recursion into a convolution
identity for the Taylor coefficients of $F(t) = H(t)/t^2$,
showing $F^2 = Q$.  The orders $m = 0, 1, 2$ of this identity
reproduce the definitions of $\kappa$, $\alpha$, $S_4$; the
orders $m \ge 3$ are exactly the recursion.

This is the \emph{intrinsic quartic principle}: an infinite
sequence of invariants, one for each arity $r \ge 2$, is
determined by three numbers.  The situation is analogous to the
role of the Weierstrass equation for an elliptic curve: two
parameters $(g_2, g_3)$ determine all Laurent coefficients
of~$\wp$, because $\wp$ satisfies an algebraic equation of
degree~$2$ in $\wp'$.  Here, three parameters
$(\kappa, \alpha, S_4)$ determine all shadow coefficients
$S_r$, because $H$ satisfies an algebraic equation of
degree~$2$ in~$H$.

\subsection{The four-class classification}

Write
$Q(t) = (2\kappa + 3\alpha t)^2 + 2\Delta\,t^2$
for the \emph{Gaussian decomposition}, where
$\Delta := 8\kappa S_4$ is the \emph{critical discriminant}.
The Gaussian envelope $(2\kappa + 3\alpha t)^2$ is the part
of~$Q$ visible to the quadratic and cubic shadows alone;
$\Delta$ measures the irreducible quartic contribution.

The critical discriminant controls a fundamental dichotomy.

When $\Delta = 0$, the shadow metric is a perfect square:
$Q = (2\kappa + 3\alpha t)^2$, the generating function
$H(t) = t^2(2\kappa + 3\alpha t)$ is polynomial, and the
tower terminates.  If $\alpha = 0$, only $S_2 = \kappa$ survives
(depth~$2$); if $\alpha \ne 0$, then $S_2$ and $S_3$ survive
(depth~$3$).

When $\Delta \ne 0$, the shadow metric is irreducible:
$\sqrt{Q}$ is irrational, every Taylor coefficient of $\sqrt{Q}$
beyond degree~$1$ carries a factor of~$\Delta$, and $S_r \ne 0$
for all $r \ge 4$ (generically).  The tower is infinite.

This yields the second main result
(Theorem~\ref{thm:main}, part~(iii)): every chirally Koszul
algebra whose primary-line shadow data has been computed falls
into one of four \emph{shadow depth classes}.  The partition
is exhaustive for the standard Lie-theoretic landscape
(Table~\ref{tab:master-shadow}); whether every chirally Koszul
algebra belongs to one of these four classes is a structural
observation, not a classification theorem.

\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lccll@{}}
\toprule
Class & $\Delta$ & $r_{\max}$ & Prototype & Shadow data \\
\midrule
$\mathbf{G}$ (Gaussian) & $0$ & $2$ & Heisenberg & $\kappa = k$ \\
$\mathbf{L}$ (Lie) & $0$ & $3$ & Affine Kac--Moody &
$\kappa,\,\alpha \ne 0$ \\
$\mathbf{C}$ (Contact) & $0^*$ & $4$ & $\beta\gamma$ system &
$\kappa = 6\lambda^2{-}6\lambda{+}1$ \\
$\mathbf{M}$ (Mixed) & $\ne 0$ & $\infty$ & Virasoro, $\mathcal{W}_N$ &
$\kappa,\,\alpha,\,S_4$ \\
\bottomrule
\multicolumn{5}{@{}l}{\footnotesize ${}^*$Class $\mathbf{C}$:
$\Delta = 0$ on the primary line; the quartic contact invariant
lives on a charged stratum.}
\end{tabular}
\end{center}

\noindent
Class~$\mathbf{G}$ consists of algebras whose bar
complex is formal in the classical sense: the shadow obstruction tower
terminates at the leading scalar, and all higher-genus free
energies $F_g$ are determined by~$\kappa$ alone.
Class~$\mathbf{L}$ adds exactly one cubic correction (the
structure constant of the Lie bracket on generators), after which
the tower terminates by the Jacobi identity.
Class~$\mathbf{C}$ is the first nonlinear class: the quartic
contact invariant~$S_4$ is nonzero but lives on a separate
stratum whose self-bracket exits the complex, so the tower
terminates after one further step.
Class~$\mathbf{M}$ is the generic class: the shadow obstruction tower is
infinite, the free energies $F_g$ receive corrections at every
arity, and the shadow coefficients $S_r$ decay (or grow) at a
computable rate governed by the \emph{shadow growth rate}
\begin{equation}\label{eq:intro-growth-rate}
  \rho(\cA)
  \;=\;
  \sqrt{\frac{9\alpha^2 + 16\kappa S_4}{4\kappa^2}}.
\end{equation}

The growth rate is the reciprocal of the branch-point modulus
of the shadow metric.  When $\rho < 1$, the shadow obstruction tower converges
absolutely; when $\rho > 1$, it diverges but the algebraic
function $\sqrt{Q}$ extends analytically past the convergence
radius.  For the Virasoro algebra at central charge~$c$:
\begin{equation}\label{eq:intro-virasoro-rho}
  \rho(\Vir_c)
  \;=\;
  \frac{1}{c}\sqrt{\frac{180c + 872}{5c + 22}},
\end{equation}
with a critical central charge $c_\star \approx 6.125$ (the
unique positive root of $5c^3 + 22c^2 - 180c - 872 = 0$)
separating the convergent and divergent regimes.  At the
self-dual point $c = 13$ (where $\Vir_c^! = \Vir_{26-c}$ satisfies
$\Vir_c = \Vir_c^!$): $\rho \approx 0.467$.

Classical Koszul duality over a point is the genus-$0$,
arity-$2$, $\Delta = 0$ stratum of this picture: the formal
Gaussian case where the tower terminates immediately.  Everything
beyond class~$\mathbf{G}$ is new.

\subsection{The shadow connection and Koszul monodromy}

The shadow metric equips each primary line with a logarithmic
connection
\begin{equation}\label{eq:intro-connection}
  \nabla^{\mathrm{sh}}
  \;=\;
  d \;-\; \frac{Q'(t)}{2\,Q(t)}\,dt,
\end{equation}
with regular singularities at the zeros of~$Q$ and residue
$\frac{1}{2}$.  The monodromy around each branch point is~$-1$.
This is the \emph{Koszul sign}: the square root $\sqrt{Q}$
changes sign around a simple zero, and the shadow obstruction tower inherits
this sign change through the algebraic relation
$H = t^2\sqrt{Q}$.

Under Koszul duality $\cA \mapsto \cA^!$, the shadow metric
transforms by the Verdier involution.  For the Virasoro family
$\Vir_c^! = \Vir_{26-c}$, the discriminants satisfy
\begin{equation}\label{eq:intro-disc-complementarity}
  \Delta(\Vir_c) + \Delta(\Vir_{26-c})
  \;=\;
  \frac{6960}{(5c + 22)(152 - 5c)},
\end{equation}
a Virasoro-specific identity whose numerator
$6960 = 40 \cdot 174$ is a product of the Virasoro quartic
normalization and the sum of the Lee--Yang denominators.
The Koszul dual singularities $c = -22/5$ and $c = 152/5$
sum to~$26$: they are Koszul partners.  For other families
(affine Kac--Moody, $\cW_N$ with $N \ge 3$), the
discriminant sum has a different numerator.

\subsection{Genus-$2$ free energies}

The shadow obstruction tower produces invariants of moduli spaces by
evaluating graph sums over stable curves.  The genus-$g$
\emph{free energy}
$F_g(\cA) = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}$
is computed for each chirally Koszul algebra by the
\emph{Faber--Pandharipande integral}
$\lambda_g^{\mathrm{FP}} = \int_{\overline{\cM}_g} \lambda_g$,
where $\lambda_g = c_g(\mathbb{E})$ is the top Chern class
of the Hodge bundle.

At genus~$2$: $\lambda_2^{\mathrm{FP}} = 7/5760$, and
$F_2(\cA) = \kappa \cdot 7/5760$ for every single-generator
chirally Koszul algebra.  The verification requires
an explicit sum over the six stable graphs of
genus~$2$ with no marked points (the smooth genus-$2$
curve, figure-eight, banana, dumbbell, theta, and
lollipop), weighted by automorphism factors and vertex
contributions from the shadow obstruction tower.

For the $\mathcal{W}_3$ algebra, which has two generators
$T$ (weight~$2$) and $W$ (weight~$3$) producing two primary
lines, the genus-$2$ computation is a multi-channel graph sum:
each edge of the stable graph carries a channel label
($T$ or~$W$), each vertex contributes a shadow coefficient on
the corresponding primary line, and the propagator
$P_T = 2/c$, $P_W = 3/c$ depends on the channel.  The
per-channel diagonal sum yields
$F_2^{\mathrm{scal}}(\mathcal{W}_3) = \kappa \cdot \lambda_2^{\mathrm{FP}}
= 7c/6912$, but the full multi-channel graph sum produces an
additional cross-channel correction
$\delta F_2 = (c+120)/(16c)$.  Whether this correction is
cancelled by CohFT $R$-matrix terms (restoring the universality
identity $F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$ at
genus~$2$ for multi-generator algebras) is the content of the
multi-generator universality problem, which remains open.

The Maurer--Cartan equation on
$\overline{\cM}_{2,0}$ also produces a
\emph{planted-forest correction}
\begin{equation}\label{eq:intro-planted-forest}
  \delta_{\mathrm{pf}}^{(2,0)}
  \;=\;
  \frac{S_3(10\,S_3 - \kappa)}{48},
\end{equation}
measuring the contribution of codimension-$2$ boundary strata
to the genus-$2$ amplitude.  This correction vanishes for
class~$\mathbf{G}$ (where $S_3 = 0$).  For
classes~$\mathbf{C}$ and~$\mathbf{M}$, it is generically nonzero.
For the Virasoro algebra:
$\delta_{\mathrm{pf}}^{(2,0)} = -(c - 40)/48$.

\subsection{The gravitational coproduct}

The fourth result concerns the transferred algebraic structure
under BRST reduction.  The Drinfeld--Sokolov (DS) reduction
functor takes affine Kac--Moody data to $\cW$-algebra data via a
BRST complex with ghosts.  The homological perturbation lemma
(HPL) transfers the $A_\infty$ products and the coproduct from
the affine dg-shifted Yangian to a transferred Yangian on the
$\cW$-algebra sector.

We prove the result for all principal DS reductions
$\widehat{\mathfrak{sl}}_N \to \cW_N$.
The ghost-number obstruction (the homotopy~$h$ in the SDR has
ghost degree~$-1$, and the projection $p \otimes p$ kills all
ghost-number-$(-1)$ elements) forces the transferred coproduct to
be \emph{strictly primitive at all arities}.  The mechanism is
universal: the ghost-number grading of the BRST complex for any
principal DS reduction $\widehat{\fg} \to \cW(\fg)$ has the same
structure.  For $N = 2$ (the Virasoro case):
\[
  \Delta_z^{\Vir}(T)
  \;=\;
  \tau_z(T) \otimes 1 + 1 \otimes T,
  \qquad
  \Delta_{z,n}^{\Vir} = 0
  \quad\text{for } n \ge 2.
\]
All higher-arity coproduct corrections, which would represent
graviton splitting into constituent gravitons, are killed by the
ghost-number mechanism.  The only nontrivial gravitational
structure is the $r$-matrix twist
$r^{\Vir}(z) = (c/2)/z^3 + 2T/z$ on the target product,
encoding the braiding of line operators.

The physical content: in Chern--Simons gauge theory, gluons
split (the coproduct is nontrivial, reflecting the
Clebsch--Gordan decomposition of tensor products).  In
$3$d gravity, gravitons do not split.  The gravitational
coproduct is primitive; all interactions are encoded in
the twist, not in particle production.

\subsection{The Epstein zeta function of the shadow metric}

For class~$\mathbf{M}$ algebras at rational central charge,
the shadow metric~$Q_L$ is a positive definite binary quadratic
form on~$\mathbb{Z}^2$ (since
$\operatorname{disc}(Q_L) = -32\kappa^2\Delta < 0$).  Its
Epstein zeta function
\[
  \varepsilon_{Q_L}(s)
  \;:=\;
  \sideset{}{'}\sum_{(m,n) \in \mathbb{Z}^2}
  Q_L(m,n)^{-s}
\]
converges for $\operatorname{Re}(s) > 1$, extends
meromorphically, and satisfies the functional equation
$\Lambda_{Q_L}(s) = \Lambda_{Q_L}(1 - s)$ after the standard
gamma completion~\cite{Epstein1903, Terras73}.  The
discriminant of~$Q_L$ determines an imaginary quadratic
extension $K_L = \mathbb{Q}(\sqrt{D_0})$, the \emph{shadow
field}.  When the class number $h(D_0) = 1$, the Epstein
zeta factors through the Dedekind zeta of~$K_L$, which in
turn splits as $\zeta_{K_L}(s) = \zeta(s) \cdot L(s, \chi_d)$.
The chain
\begin{equation}\label{eq:intro-shadow-field-chain}
  \cA
  \;\xrightarrow{\;\text{shadow obstruction tower}\;}
  Q_L
  \;\xrightarrow{\;\operatorname{disc}\;}
  D_0
  \;\xrightarrow{\;\mathbb{Q}(\sqrt{\cdot})\;}
  K_L
  \;\xrightarrow{\;\zeta_K\;}
  L(s, \chi_d)
\end{equation}
produces a Dirichlet $L$-function from OPE data.  For the
Ising model ($c = 1/2$): the shadow field is
$\mathbb{Q}(\sqrt{-10})$.  For class~$\mathbf{G}$ and
class~$\mathbf{L}$ algebras, $\Delta = 0$ forces the
discriminant to vanish and the construction degenerates.
This is the shadow-theoretic meaning of the G/L/C/M
partition: classes~$\mathbf{G}$ and~$\mathbf{L}$ have
trivial arithmetic content, while class~$\mathbf{M}$ produces
genuine number-theoretic invariants.

\subsection{The $E_8$ decisive test}

The bar complex makes a prediction for every lattice vertex
algebra at every genus.  At genus~$2$ for the $E_8$ lattice:
$F_2(V_{E_8}) = 8 \cdot 7/5760 = 7/720$.  This prediction
is verified by three independent methods:
(a)~the bar-complex formula $F_2 = \kappa \cdot \lambda_2^{\mathrm{FP}}$;
(b)~the Siegel--Weil formula with Cohen--Katsurada coefficients
($\Theta_{E_8}^{(2)} = E_4^{(2)}$, giving
$a(I_2) = 240 \times 126 = 30240$);
(c)~direct lattice enumeration.
The three-way agreement is a nontrivial consistency check:
the bar complex knows, from purely algebraic data, that each
of the $240$ $E_8$ roots has exactly~$126$ orthogonal partners.

\subsection{The descent fan}

The MC element $\Theta_\cA$ projects onto three mathematical
worlds.  These projections share a common source but do not
compose into a single functor: the ``descent chain'' is a
\emph{fan}, not a chain.

\begin{enumerate}[(i)]
\item \emph{Categorical projection.}
  $\cA \mapsto \barB^{\mathrm{ch}}(\cA) \mapsto \cA^!$.
  Target: factorization coalgebras and their Verdier duals.
  Symmetry: the Koszul involution $\cA \leftrightarrow \cA^!$.

\item \emph{Spectral projection.}
  $\cA \mapsto \{S_r\} \mapsto \sqrt{Q_L} \mapsto
  \varepsilon_{Q_L}(s)$.
  Target: the shadow obstruction tower and the Epstein zeta.
  Symmetry: the functional equation $s \leftrightarrow 1 - s$.

\item \emph{Modular projection.}
  $\cA \mapsto Z_g(\cA) \mapsto S_\cA(v)$.
  Target: the genus expansion and the sewing partition function.
  Symmetry: the Galois involution on the $L$-function content.
\end{enumerate}
The Koszul involution, the functional equation involution, and
the Galois involution are three different involutions on three
different spaces.  No functor intertwines all three.

\subsection{What is proved, what is open}

The following is a candid assessment.

\emph{Proved unconditionally}: the algebraicity theorem
(Theorem~\ref{thm:main}(i)--(ii)); the four-class
classification; the genus-$g$ formula
$F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$ for all
single-generator chirally Koszul algebras at all genera;
the genus-$1$ universality $F_1 = \kappa/24$ for all
families including multi-generator; the gravitational
coproduct primitivity for all principal DS reductions;
the Epstein zeta functional equation for class~$\mathbf{M}$
at rational~$c$.

\emph{Open}: whether $F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$
holds at genus~$g \ge 2$ for multi-generator algebras
(the multi-generator universality problem).  The
genus-$2$ $\cW_3$ computation
(\S\ref{sec:genus2-w3}) exhibits the cross-channel
correction that any proof must cancel.  Whether
the Koszul--Epstein zeta has zeros on a single critical
line is completely open; it requires understanding the
arithmetic of the shadow field at a level far beyond
the present methods.

\subsection{Relation to existing work}

The bar construction for chiral algebras was introduced by
Beilinson and Drinfeld~\cite{BD04} and developed in the
factorization algebra framework by Francis and Gaitsgory
\cite{FG12} and Costello and Gwilliam~\cite{CG17}.
The modular characteristic~$\kappa$ appears implicitly in the
work of Feigin and Fuchs on Hodge bundles of conformal blocks,
and the formula $\kappa(\Vir_c) = c/2$ can be extracted from
Beilinson and Schechtman~\cite{BS88}.
The invariants of moduli spaces produced by vertex algebras via
conformal blocks are the subject of Faber and
Pandharipande~\cite{FP00}, Mumford~\cite{Mumford83}, and the
extensive literature on cohomological field theories following
Kontsevich and Manin~\cite{KM94}.  The Epstein zeta function
of a binary quadratic form is due to Epstein~\cite{Epstein1903};
the functional equation and Bessel-series expansion are due
to Terras~\cite{Terras73}.  The connection between conformal
field theory and the scalar modular bootstrap is studied
by Benjamin and Chang~\cite{BenjaminChang22}.

The quartic shadow $S_4$, the critical discriminant~$\Delta$,
the four-class partition, the algebraicity theorem
(Theorem~\ref{thm:main}), the shadow field, and the
Koszul--Epstein construction appear to be new.  The connection
between shadow depth and $L_\infty$ non-formality, while
consonant with the general philosophy of Kontsevich~\cite{Kontsevich03},
has not been established previously in the chiral setting.

The Drinfeld--Sokolov reduction and its homological algebra are
classical \cite{KRW03, FF90, DS85};
the gravitational coproduct primitivity result
(Theorem~\ref{thm:grav-primitivity-standalone}) and its connection to the
shadow obstruction tower appear to be new.

\subsection{Structure of the paper}

Section~\ref{sec:background} reviews chiral algebras, the bar
construction, and the modular characteristic, establishing
notation and the three seed invariants
$(\kappa, \alpha, S_4)$.
Section~\ref{sec:convolution} defines the modular convolution
algebra and the Maurer--Cartan element~$\Theta_\cA$.
Section~\ref{sec:shadow-metric} introduces the shadow
metric and the recursion on primary lines.
Section~\ref{sec:algebraicity} proves the Riccati algebraicity
theorem, derives the shadow connection, the depth
classification, and the growth rate.
Section~\ref{sec:four-classes} presents the four shadow
classes with explicit examples and the master shadow table.
Section~\ref{sec:shadow-tables} records the complete shadow
tables for the standard landscape, including the
complementarity data and the Virasoro tower through arity~$10$.
Section~\ref{sec:genus2-w3} carries out the genus-$2$ graph sum
for~$\cW_3$, including the multi-channel cross-channel correction
and the planted-forest formula.
Section~\ref{sec:gravitational-coproduct} proves the gravitational
coproduct primitivity for all principal DS reductions.
Section~\ref{sec:e8-test} verifies the $E_8$ decisive test.
Section~\ref{sec:epstein} develops the Epstein zeta function
of the shadow metric and the shadow field construction.
Section~\ref{sec:outlook} discusses the descent fan, the
Koszul--Epstein frontier, and open problems.


% ================================================================
%  Body sections
% ================================================================

\section{Chiral Koszul pairs and the bar construction}
\label{sec:background}

Let $X$ be a smooth projective curve of genus~$g$ over an
algebraically closed field~$k$ of characteristic zero.
A \emph{chiral algebra} on~$X$ is a $\mathcal{D}_X$-module
$\cA$ equipped with a chiral bracket
$\mu \colon j_* j^* (\cA \boxtimes \cA)
\to \Delta_! \cA$, where $j \colon X^2 \setminus \Delta
\hookrightarrow X^2$ is the complement of the diagonal and
$\Delta_!$ is the $!$-pushforward~\cite{BD04}.  On the formal
disc, the chiral bracket encodes the operator product expansion
$\phi^a(z)\,\phi^b(w) \sim \sum_{n \ge 0}
(\phi^a{}_{(n)}\phi^b)(w)/(z-w)^{n+1}$.

The \emph{chiral bar construction}
$\barB^{\mathrm{ch}}(\cA) = \bigoplus_{n \ge 1}
\cA^{\boxtimes n}[-1]^{\otimes n}$ is a factorization coalgebra
on the Ran space $\Ran(X)$, with differential
$d = \sum_{i < j} d_{ij}$ built from the OPE residues
weighted by the kernel $\eta_{ij} = d\log(z_i - z_j)$ on the
Fulton--MacPherson compactification~\cite{FG12, CG17}.
The bar complex is \emph{chirally Koszul} if
$H^*(\barB^{\mathrm{ch}}(\cA))$ is concentrated in bar
degree~$1$.

The \emph{modular characteristic} of~$\cA$ is the scalar
$\kappa(\cA) \in \mathbb{Q}(c)$ defined by the genus-$1$
identity $F_1(\cA) = \kappa(\cA)/24$.  It controls the
bar curvature: $d^2|_{\text{fib}} = \kappa \cdot \omega_g$,
where $\omega_g = c_1(\mathbb{E})$ is the Hodge class.
Explicit formulas: $\kappa(\mathcal{H}_k) = k$,
$\kappa(V_k(\fg)) = \dim(\fg)(k + h^\vee)/(2h^\vee)$,
$\kappa(\Vir_c) = c/2$, $\kappa(\cW_N) = c(H_N - 1)$.

The \emph{cubic shadow} $\alpha = S_3$ measures the transferred
$L_\infty$ bracket~$\ell_3$ on bar cohomology: it is the
structure constant of the three-point collision residue.  The
\emph{quartic shadow} $S_4$ is the contact term of the
four-point collision, computed from the quartic OPE data.
These three numbers $(\kappa, \alpha, S_4)$ are the seed
invariants of the paper.

\section{The modular convolution algebra}
\label{sec:convolution}

The bar complex on a curve of genus~$g$ with~$n$ marked points
defines a pronilpotent dg Lie algebra
$\gmod$ (the modular convolution algebra), whose differential
encodes graph sums over stable curves.  The construction proceeds
in three steps.

\emph{Step 1: the coefficient algebra.}
Let $G_{\mathrm{st}}$ denote the species of stable graphs
$\Gamma = (V, E, g \colon V \to \mathbb{Z}_{\ge 0})$ with
genus function~$g$ and the stability condition
$2g_v + \mathrm{val}_v \ge 3$ at each vertex.  The stable-graph
coefficient algebra is
$\mathfrak{G}_{\mathrm{st}} = \bigoplus_\Gamma
\mathbb{Q} \cdot [\Gamma] / \mathrm{Aut}(\Gamma)$,
graded by $h^1(\Gamma) + \sum_v g_v$.

\emph{Step 2: convolution.}
The modular convolution dg Lie algebra is
$\gmod = \Hom(\mathfrak{G}_{\mathrm{st}}, \Defcyc(\cA))$,
with bracket from graph composition (inserting a graph at a
vertex of another) and differential from the boundary-of-boundary
relation $\partial^2 = 0$ on $\overline{\cM}_{g,n}$.

\emph{Step 3: the MC element.}
The boundary relation $\partial^2 = 0$ implies $D^2 = 0$ on
$\gmod$.  The element $\Theta_\cA := D_\cA - d_0$ is
therefore a Maurer--Cartan element:
$D\Theta_\cA + \tfrac{1}{2}[\Theta_\cA, \Theta_\cA] = 0$.
Its finite-order projections $\Theta_\cA^{\le r}$ form the
shadow Postnikov tower.

\begin{theorem}[Main theorem]\label{thm:main}
Let\/ $\cA$ be a chirally Koszul vertex algebra on a smooth
projective curve with modular characteristic $\kappa$,
cubic shadow~$\alpha$, and quartic shadow~$S_4$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Algebraicity}
  \textup{(}Theorem~\textup{\ref{thm:riccati-algebraicity}}\textup{)}.
  $H(t)^2 = t^4 Q_L(t)$, where
  $Q_L = 4\kappa^2 + 12\kappa\alpha\,t
  + (9\alpha^2 + 16\kappa S_4)\,t^2$.
\item \textbf{Classification}
  \textup{(}Theorem~\textup{\ref{thm:single-line-dichotomy}}\textup{)}.
  $r_{\max} \in \{2, 3, 4, \infty\}$.
\item \textbf{Gravitational primitivity}
  \textup{(}Theorem~\textup{\ref{thm:grav-primitivity-standalone}}\textup{)}.
  $\Delta_{z,k}^{\cW(\fg)} = 0$ for all $k \ge 2$.
\item \textbf{Epstein zeta}
  \textup{(}Theorem~\textup{\ref{thm:shadow-epstein}}\textup{)}.
  $\Lambda_{Q_L}(s) = \Lambda_{Q_L}(1-s)$.
\item \textbf{$E_8$ test}
  \textup{(}Theorem~\textup{\ref{thm:e8-three-way}}\textup{)}.
  $F_2(V_{E_8}) = 7/720$.
\end{enumerate}
\end{theorem}

\input{riccati}

\input{classification}

\input{computations}


% ================================================================
%  The E_8 decisive test
% ================================================================

\section{The $E_8$ decisive test}
\label{sec:e8-test}

The bar complex makes a prediction for every lattice vertex
algebra at every genus.  At genus~$2$ for the $E_8$ lattice,
this prediction meets classical number theory.

\subsection{The prediction}

The $E_8$ lattice is even unimodular of rank~$8$.  The vertex
algebra $V_{E_8}$ is class~$\mathbf{G}$ (Gaussian: freely
generated, $\alpha = 0$, $S_4 = 0$) with $\kappa = 8$.
The genus-$2$ formula gives:
\begin{equation}\label{eq:e8-f2}
  F_2(V_{E_8})
  \;=\;
  8 \cdot \frac{7}{5760}
  \;=\;
  \frac{7}{720}.
\end{equation}

\subsection{Verification via Siegel--Weil}

By the Siegel--Weil formula, the genus-$2$ theta function of
any even unimodular lattice of rank~$r$ equals the genus-$2$
Siegel Eisenstein series:
$\Theta_\Lambda^{(2)}(\Omega) = E_{r/2}^{(2)}(\Omega)$.
For $E_8$: $\Theta_{E_8}^{(2)} = E_4^{(2)}$.

The Fourier coefficient $a(T)$ for
$T = I_2 = \bigl(\begin{smallmatrix} 1 & 0 \\
0 & 1 \end{smallmatrix}\bigr)$ counts pairs of orthogonal
roots.  The $E_8$ root system has $240$ roots.  For each
root~$v$, the roots of~$E_8$ partition into:
\begin{enumerate}[(i)]
\item $v$ itself: $1$.
\item $-v$: $1$ (inner product~$-2$).
\item Roots $w$ with $\langle v, w \rangle = \pm 1$: $112$
  (the root system of the stabilizer subalgebra~$E_7$).
\item Orthogonal roots: $240 - 1 - 1 - 112 = 126$.
\end{enumerate}
Therefore $a(I_2) = 240 \times 126 = 30240$.

\begin{theorem}[$E_8$ genus-$2$ three-way agreement]
\label{thm:e8-three-way}
The identity $F_2(V_{E_8}) = 7/720$ is verified by:
\begin{enumerate}[\textup{(}a\textup{)}]
\item the bar-complex formula
  $F_2 = \kappa \cdot \lambda_2^{\mathrm{FP}}$;
\item the Siegel--Weil formula with Cohen--Katsurada
  coefficients;
\item direct lattice enumeration \textup{(}$240 \times 126
  = 30240$\textup{)}.
\end{enumerate}
\end{theorem}

\begin{proof}
The genus-$2$ partition function decomposes as
$Z_2 = \Theta_{E_8}^{(2)} \cdot Z_2^{\mathrm{osc}}$, where
$\Theta_{E_8}^{(2)} = E_4^{(2)}$ by Siegel--Weil and
$Z_2^{\mathrm{osc}}$ is the oscillator contribution.
The Mumford isomorphism gives
$F_g^{\mathrm{osc}} = r \cdot \lambda_g^{\mathrm{FP}}$ with
$r = \operatorname{rank}(\Lambda) = 8$, recovering
$F_2 = 8 \cdot 7/5760 = 7/720$.  The lattice count
$240 \times 126$ is the same number expressed as
$a(I_2)$ of the Siegel modular form~$E_4^{(2)}$.
\end{proof}

The bar complex knows, from purely algebraic data (the OPE
and the modular characteristic~$\kappa = 8$), that each of the
$240$ $E_8$ roots has exactly~$126$ orthogonal partners.  No
root system or lattice enumeration enters the algebraic
prediction; it enters only the verification.


% ================================================================
%  The Epstein zeta function of the shadow metric
% ================================================================

\section{The Epstein zeta function of the shadow metric}
\label{sec:epstein}

\subsection{The shadow metric as a binary quadratic form}

For a class~$\mathbf{M}$ algebra at rational central charge~$c$,
the shadow metric
$Q_L(t) = 4\kappa^2 + 12\kappa\alpha\,t
+ (9\alpha^2 + 2\Delta)\,t^2$
is a quadratic polynomial in~$t$ with rational coefficients,
positive leading coefficient ($4\kappa^2 > 0$), and negative
discriminant ($\operatorname{disc}(Q_L) = -32\kappa^2\Delta < 0$
since $\Delta > 0$ for the standard families at positive~$c$).
Interpreting $Q_L$ as a binary quadratic form
$Q_L(m, n) = 4\kappa^2 m^2 + 12\kappa\alpha\, mn
+ (9\alpha^2 + 2\Delta)\, n^2$
on~$\mathbb{Z}^2$, the form is positive definite.

\begin{theorem}[Epstein zeta of the shadow metric]
\label{thm:shadow-epstein}
Let $\cA$ be a class~$\mathbf{M}$ chirally Koszul algebra
at rational~$c$ with shadow metric~$Q_L$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item The \emph{Epstein zeta function}
\begin{equation}\label{eq:shadow-epstein}
  \varepsilon_{Q_L}(s)
  \;:=\;
  \sideset{}{'}\sum_{(m,n) \in \mathbb{Z}^2}
  Q_L(m,n)^{-s},
  \qquad
  \operatorname{Re}(s) > 1,
\end{equation}
converges absolutely for $\operatorname{Re}(s) > 1$ and
extends to a meromorphic function on~$\mathbb{C}$ with a
simple pole at $s = 1$ of residue
$2\pi/\sqrt{|\operatorname{disc}(Q_L)|}$.

\item The completed function
$\Lambda_{Q_L}(s)
:= (|\operatorname{disc}(Q_L)|/(4\pi^2))^{s/2}\,
\Gamma(s)\,\varepsilon_{Q_L}(s)$
satisfies the functional equation
\begin{equation}\label{eq:shadow-fe}
  \Lambda_{Q_L}(s) = \Lambda_{Q_L}(1 - s).
\end{equation}

\item For classes $\mathbf{G}$ and $\mathbf{L}$
\textup{(}$\Delta = 0$\textup{)}, the form~$Q_L$ degenerates
and the Epstein zeta is not defined as a lattice sum of a
positive definite form.
\end{enumerate}
\end{theorem}

\begin{proof}
Classical~\cite{Epstein1903, Terras73}.  The proof uses
Poisson summation on~$\mathbb{Z}^2$: writing
$Q_L(m,n) = (m,n)\,A\,(m,n)^T$ with the matrix
$A = \bigl(\begin{smallmatrix}
  4\kappa^2 & 6\kappa\alpha \\
  6\kappa\alpha & 9\alpha^2 + 2\Delta
\end{smallmatrix}\bigr)$,
the Mellin transform of the theta function
$\vartheta_{Q_L}(\tau) :=
\sum_{(m,n)} e^{-\pi\tau\,Q_L(m,n)}$
and the standard unfolding argument (splitting the integral
at $\tau = 1$) yield the functional equation.
\end{proof}

\subsection{The shadow field}

\begin{definition}[Shadow field]
\label{def:shadow-field}
For a class~$\mathbf{M}$ algebra at rational~$c$, the
\emph{shadow field} is the imaginary quadratic extension
$K_L := \mathbb{Q}(\sqrt{D_0})$,
where $D_0$ is the squarefree part of
$\operatorname{disc}(Q_L) = -32\kappa^2\Delta$.
\end{definition}

When the class number $h(D_0) = 1$, the Epstein zeta factors
through the Dedekind zeta of~$K_L$:
$\varepsilon_{Q_L}(s) = c_0 \cdot \zeta_{K_L}(s)$
for an explicit constant~$c_0$.  The Dedekind zeta then splits:
$\zeta_{K_L}(s) = \zeta(s) \cdot L(s, \chi_d)$,
where $d$ is the fundamental discriminant and $\chi_d$ the
Kronecker character.  The chain
\[
  \cA
  \;\xrightarrow{\;\text{shadow}\;}
  Q_L
  \;\xrightarrow{\;\operatorname{disc}\;}
  D_0
  \;\xrightarrow{\;\mathbb{Q}(\sqrt{\cdot})\;}
  K_L
  \;\xrightarrow{\;\zeta_K\;}
  L(s, \chi_d)
\]
produces a Dirichlet $L$-function from OPE data.

\subsection{The shadow field table}

The shadow field data for the Virasoro algebra at selected
rational values of~$c$ is recorded in
Table~\ref{tab:shadow-fields-vir}
(Section~\ref{sec:four-classes}).  The squarefree kernel~$D_0$
of $\operatorname{disc}(Q_L) = -320c^2/(5c+22)$ determines
$K_L = \mathbb{Q}(\sqrt{D_0})$.  For the Ising model:
$D_0 = -10$, so $K_L = \mathbb{Q}(\sqrt{-10})$, with
class number $h(-10) = 2$.

The functional equation of the Epstein zeta is a spectral
shadow of Koszul duality: it interchanges $c$ and~$c'$,
and the symmetric point $s = 1/2$ of the completed functional
equation corresponds to the self-dual central charge $c = 13$
where $\Vir_c = \Vir_c^!$.

\begin{remark}[The Koszul--Epstein frontier]
\label{rem:koszul-epstein-frontier}
The deepest open question at the intersection of the algebraic
and arithmetic theories: \emph{does the Koszul--Epstein zeta
function $\varepsilon_{Q_L}(s)$ have all its zeros on a
critical line?}  For class~$\mathbf{M}$ algebras,
$\varepsilon_{Q_L}$ is an Epstein zeta function of a
positive definite binary quadratic form.  The Davenport--Heilbronn
theorem~\cite{DavenportHeilbronn36} shows that Epstein zeta
functions of forms with class number $h > 1$ can have zeros
off the critical line.  The shadow field at the Ising model
has discriminant~$-20$, with class number $h(-20) = 2$; thus
the Ising Epstein zeta may have off-critical zeros.  Whether
such zeros have physical meaning (as resonances, instabilities,
or phase transitions in the shadow obstruction tower) is entirely unknown.
The question connects the algebraic engine (bar complex,
Maurer--Cartan, shadow metric) to the deepest problems in
analytic number theory via a single quadratic form.
\end{remark}


% ================================================================
%  Outlook
% ================================================================

\section{Open problems and outlook}\label{sec:outlook}

\subsection{The descent fan}

The MC element $\Theta_\cA$ admits three independent
projections with distinct targets and distinct symmetries:
\begin{enumerate}[(i)]
\item \emph{Categorical.}
  $\cA \to \barB^{\mathrm{ch}}(\cA) \to \cA^!$.
  The Koszul involution $\cA \leftrightarrow \cA^!$.
\item \emph{Spectral.}
  $\cA \to \{S_r\} \to \sqrt{Q_L} \to \varepsilon_{Q_L}(s)$.
  The functional equation $s \leftrightarrow 1 - s$.
\item \emph{Modular.}
  $\cA \to Z_g(\cA) \to S_\cA(v)$.
  The Galois involution on the $L$-function content.
\end{enumerate}
These three projections share $\Theta_\cA$ as common source
but do not compose into a single functor.  The Koszul,
functional-equation, and Galois involutions are three different
involutions on three different spaces.  For lattice VOAs, all
three projections are compatible (the lattice fan is closed);
for class~$\mathbf{M}$ algebras, the compatibility is open.

\subsection{Multi-generator universality}

Whether $F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$ holds at
genus~$g \ge 2$ for multi-generator algebras remains open.
The genus-$2$ $\cW_3$ computation
(\S\ref{sec:genus2-w3}) exhibits the cross-channel
correction $(c+120)/(16c)$ that must be cancelled by
CohFT $R$-matrix terms if universality holds.
The decisive evidence would be a direct genus-$2$
multi-channel graph sum with $R$-dressed propagators.

\subsection{The operadic complexity conjecture}

The shadow depth $r_{\max}(\cA)$ is conjectured to equal the
$A_\infty$-depth (the smallest~$n$ such that $m_k = 0$ for
$k > n$ in some $A_\infty$ model) and the $L_\infty$-formality
level (the smallest~$n$ such that $\ell_k = 0$ for $k > n$ on
bar cohomology).  This is proved at arities~$2$, $3$, $4$; the
general statement is open.

\subsection{Pixton's ideal}

Class~$\mathbf{M}$ algebras generate an infinite sequence of
tautological classes on $\overline{\cM}_g$ via the MC tower.
Whether these classes generate Pixton's ideal (the kernel of
the tautological ring surjection) is a deep structural
conjecture connecting the shadow obstruction tower to the geometry of
moduli spaces.


% ================================================================
%  References (placeholder)
% ================================================================

\begin{thebibliography}{99}

\bibitem{BD04}
A.~Beilinson and V.~Drinfeld,
\textit{Chiral Algebras},
AMS Colloquium Publications, vol.~51,
American Mathematical Society, Providence, RI, 2004.

\bibitem{BenjaminChang22}
N.~Benjamin and C.-H.~Chang,
Scalar modular bootstrap and zeros of the Riemann zeta function,
arXiv:2208.02259, 2022.

\bibitem{BGS96}
A.~Beilinson, V.~Ginzburg, and W.~Soergel,
Koszul duality patterns in representation theory,
\textit{J.~Amer.\ Math.\ Soc.}~\textbf{9} (1996), 473--527.

\bibitem{BS88}
A.~Beilinson and V.~Schechtman,
Determinant bundles and Virasoro algebras,
\textit{Comm.\ Math.\ Phys.}~\textbf{118} (1988), 651--701.

\bibitem{CG17}
K.~Costello and O.~Gwilliam,
\textit{Factorization Algebras in Quantum Field Theory},
vols.~1--2, Cambridge University Press, 2017/2021.

\bibitem{DavenportHeilbronn36}
H.~Davenport and H.~Heilbronn,
On the zeros of certain Dirichlet series,
\textit{J.~London Math.\ Soc.}~\textbf{11} (1936), 181--185,
307--312.

\bibitem{DS85}
V.~Drinfeld and V.~Sokolov,
Lie algebras and equations of Korteweg--de Vries type,
\textit{J.~Soviet Math.}~\textbf{30} (1985), 1975--2036.

\bibitem{Epstein1903}
P.~Epstein,
Zur Theorie allgemeiner Zetafunktionen,
\textit{Math.\ Ann.}~\textbf{56} (1903), 615--644.

\bibitem{FG12}
J.~Francis and D.~Gaitsgory,
Chiral Koszul duality,
\textit{Selecta Math.\ (N.S.)}~\textbf{18} (2012), 27--87.

\bibitem{FP00}
C.~Faber and R.~Pandharipande,
Hodge integrals and moduli spaces of curves,
in \textit{Moduli of Curves and Abelian Varieties},
Aspects Math.~E33, Vieweg, 2000, pp.~109--130.

\bibitem{FF90}
B.~Feigin and E.~Frenkel,
Quantization of the Drinfeld--Sokolov reduction,
\textit{Phys.\ Lett.\ B}~\textbf{246} (1990), 75--81.

\bibitem{FlajoletSedgewick}
P.~Flajolet and R.~Sedgewick,
\textit{Analytic Combinatorics},
Cambridge University Press, 2009.

\bibitem{KhanZeng25}
A.~Z.~Khan and K.~Zeng,
Poisson vertex algebras and three-dimensional gauge theory,
arXiv:2502.13227, 2025.

\bibitem{KM94}
M.~Kontsevich and Yu.~Manin,
Gromov--Witten classes, quantum cohomology, and enumerative geometry,
\textit{Comm.\ Math.\ Phys.}~\textbf{164} (1994), 525--562.

\bibitem{Kontsevich03}
M.~Kontsevich,
Deformation quantization of Poisson manifolds,
\textit{Lett.\ Math.\ Phys.}~\textbf{66} (2003), 157--216.

\bibitem{KRW03}
V.~Kac, S.-S.~Roan, and M.~Wakimoto,
Quantum reduction for affine superalgebras,
\textit{Comm.\ Math.\ Phys.}~\textbf{241} (2003), 307--342.

\bibitem{Lorgat}
R.~Lorgat,
\textit{Modular Koszul Duality},
in preparation (monograph, two volumes).

\bibitem{LV12}
J.-L.~Loday and B.~Vallette,
\textit{Algebraic Operads},
Grundlehren der Mathematischen Wissenschaften, vol.~346,
Springer, Berlin, 2012.

\bibitem{Mumford83}
D.~Mumford,
Towards an enumerative geometry of the moduli space of curves,
in \textit{Arithmetic and Geometry, Vol.~II},
Progr.\ Math., vol.~36, Birkh\"auser, 1983, pp.~271--328.

\bibitem{Priddy70}
S.~Priddy,
Koszul resolutions,
\textit{Trans.\ Amer.\ Math.\ Soc.}~\textbf{152} (1970), 39--60.

\bibitem{Terras73}
A.~Terras,
Bessel series expansions of the Epstein zeta function
and the functional equation,
\textit{Trans.\ Amer.\ Math.\ Soc.}~\textbf{183} (1973), 477--486.

\end{thebibliography}

\end{document}
