% wave17 / agent_02_G1_koszul_reflection.tex
% Adversarial attack-heal record on Generating Identity G1 / Theorem A.
% Target: the Koszul reflection K = barB^{ch}_X o Omega^{ch}_X satisfies
% K^2 simeq id on Kosz(X), with explicit chain-level homotopies.
% Five ATTACK-HEAL cycles, voiced as Kazhdan (compression) + Etingof (clarity)
% + Drinfeld (unifying principle) + Costello (factorisation as organising principle).
% Author: Raeez Lorgat. No AI attribution. Working scratch, NOT manuscript prose.
% Not for direct inclusion in main manuscript; this is what survives after
% adversarial audit of thm:koszul-reflection in chapters/theory/theorem_A_infinity_2.tex.
%
% Target, in compact form:
%   (Theorem A / G1)  (Omega^{ch}_X, barB^{ch}_X) : Coalg_X^{conil,comp} <-> Alg_X^{aug}
%                     is a symmetric-monoidal adjoint equivalence.
%   (local form)      On Kosz(C), K := barB^{ch}_C o Omega^{ch}_C satisfies K^2 simeq id
%                     at chain level.
%   (global form)     On Kosz^{rel}/\bar M_{g,n}, K^univ is an (infty,1)-adjoint
%                     autoequivalence with (K^univ)^2 simeq id.
%   (hypotheses)      (H1) augmentation; (H2) augmentation-ideal completeness;
%                     (H3) finite-dim graded bar pieces.

\providecommand{\ClaimStatusTheorem}{\textsc{[Theorem]}}
\providecommand{\ClaimStatusConjectured}{\textsc{[Conjectured]}}
\providecommand{\ClaimStatusHeuristic}{\textsc{[Heuristic]}}
\providecommand{\ClaimStatusScoped}{\textsc{[Scoped]}}
\providecommand{\ZZ}{\mathbb{Z}}
\providecommand{\QQ}{\mathbb{Q}}
\providecommand{\CC}{\mathbb{C}}
\providecommand{\NN}{\mathbb{N}}
\providecommand{\fg}{\mathfrak{g}}
\providecommand{\fh}{\mathfrak{h}}
\providecommand{\Ran}{\mathrm{Ran}}
\providecommand{\Conf}{\mathrm{Conf}}
\providecommand{\Sym}{\mathrm{Sym}}
\providecommand{\Bch}{B^{\mathrm{ch}}}
\providecommand{\Bbarch}{\bar{B}^{\mathrm{ch}}}
\providecommand{\Omegach}{\Omega^{\mathrm{ch}}}
\providecommand{\Kosz}{\mathsf{Kosz}}
\providecommand{\Conil}{\mathsf{Conil}}
\providecommand{\Moduli}{\overline{M}}
\providecommand{\Dmod}{\mathrm{D\text{-}mod}}
\providecommand{\Fact}{\mathrm{Fact}}
\providecommand{\Hom}{\mathrm{Hom}}
\providecommand{\id}{\mathrm{id}}
\providecommand{\Tor}{\mathrm{Tor}}
\providecommand{\Ext}{\mathrm{Ext}}
\providecommand{\CE}{\mathrm{CE}}
\providecommand{\Tw}{\mathrm{Tw}}
\providecommand{\coLie}{\mathrm{coLie}^{\mathrm{ch}}}
\providecommand{\Symch}{\mathrm{Sym}^{\mathrm{ch}}}
\providecommand{\Lambdach}{\Lambda^{\mathrm{ch}}}
\providecommand{\Virc}{\mathrm{Vir}_c}
\providecommand{\Heis}{\mathcal{H}}
\providecommand{\dGLA}{\mathrm{dGLA}}
\providecommand{\MC}{\mathrm{MC}}

\section{Adversarial attack--heal record on Theorem A / G1 (Koszul reflection)}
\label{wn:sec:wave17-opus-G1}

\textbf{Scope.} Five adversarial cycles against
Theorem~\ref{thm:koszul-reflection} in
\texttt{chapters/theory/theorem\_A\_infinity\_2.tex}. Each cycle opens
with a first-principles attack on a load-bearing assertion and closes
with what survives. The survivors carry explicit chain homotopies
witnessing $K^{2}\simeq\id$ on the three archetypal classes
$\mathsf{G}$ (Heisenberg), $\mathsf{L}$ (affine Kac--Moody at
noncritical level), $\mathsf{M}$ (Virasoro); these witness the local
chain-level form. The global form is scoped separately; the
local--global correspondence is a theorem, not a convention.

%--------------------------------------------------------------------
\subsection*{Cycle 1 (Kazhdan compression: is $K^{2}\simeq\id$ a theorem or a slogan?)}
%--------------------------------------------------------------------

\textbf{Attack.} The inscribed statement is
\[
K^{2}\;\simeq\;\id\qquad\text{on}\qquad\Kosz(X),
\]
with proof routed through ``Vallette + Positselski + Hinich +
Francis--Gaitsgory'' (four authors, one equation). Four questions.

\begin{enumerate}
\item[Q1.1] \emph{Is there an explicit chain homotopy $h$ with
$[d,h] = \id - K^{2}$, or does ``$\simeq$'' tacitly mean
``quasi-isomorphic via an unexhibited zig-zag through a cofibrant
replacement''?} If only the latter, the identity is an
$(\infty,1)$-statement with no chain-level witness.
\item[Q1.2] \emph{Where does the Koszulness hypothesis pinch?}
The bar--cobar adjunction $\Omegach\dashv\Bbarch$ is formal from the
twisting-morphism bijection \cite[Thm.\ 2.2.9]{LV12}. The
$E_{2}$-collapse of the bar--cobar spectral sequence is \emph{not}
formal; it is the content of Koszulness. What is the explicit ideal
$I\subset T^{c}(s^{-1}\bar\cA)$ whose filtration Koszulness requires?
\item[Q1.3] \emph{Is this the chiral specialisation of Priddy
(1970) or of Positselski (2011)?} Priddy's original theorem operates
on \emph{quadratic associative algebras over a field} with a PBW-type
generating family. Positselski lifts this to the coderived
category of curved CDG-coalgebras. The chiral specialisation must
pick one lane; mixing them blurs which chain-level object is actually
inverted.
\item[Q1.4] \emph{Is the statement chain-level or coderived?} The
inscription reads ``chain-level qi on $\Kosz(X)$'' in (KR-ii) but
``coderived equivalence'' in (KR-iii). What is the failure mode that
forces the separation?
\end{enumerate}

\medskip
\textbf{Heal.} The survivor keeps four distinctions.

\emph{(H1.1)} The chain homotopy $h$ exhibiting $K^{2}\simeq\id$ on
$\Kosz(X)$ is the twisted bar--cobar contracting homotopy of
Loday--Vallette \cite[\S2.3--\S2.4, eq.\ (2.17)]{LV12}, specialised to
the chiral Koszul operad.
Concretely, writing $\Bbarch_X(\cA) = T^{c}(s^{-1}\bar\cA)$ with bar
differential $d_{\Bbarch} = d_{\mathrm{int}}+d_{2}$ (internal
differential plus Hochschild-type contraction induced by the chiral
product) and $\Omegach_X(\cC) = T(s\bar\cC)$ with cobar differential
$d_{\Omegach} = d_{\mathrm{int}}+d^{\vee}_{\Delta}$ (internal plus
deconcatenation), the composite $\Omegach_X\Bbarch_X(\cA)$ carries a
canonical filtration $F_{p}\Omegach_X\Bbarch_X(\cA)$ by total bar plus
cobar length. The associated-graded is the universal twisted tensor
complex
\[
\mathrm{gr}_{F}\bigl(\Omegach_X\Bbarch_X(\cA)\bigr)
\;\cong\;
\Bbarch_X(\cA)\otimes^{\tau}\cA,
\]
with $\tau\colon\Bbarch_X(\cA)\to\cA$ the universal twisting morphism
(\cite[Prop.\ 2.1.8]{LV12}). The contracting homotopy $h$ on this
twisted tensor is \emph{concrete}: on a reduced bar-element
$s^{-1}a_{1}\otimes\cdots\otimes s^{-1}a_{n}\otimes b\in
\Bbarch_X(\cA)\otimes^{\tau}\cA$, one has
\[
h\bigl(s^{-1}a_{1}\otimes\cdots\otimes s^{-1}a_{n}\otimes b\bigr)
\;=\;
s^{-1}a_{1}\otimes\cdots\otimes s^{-1}a_{n}\otimes s^{-1}b\otimes 1,
\]
with $\id$ as the last tensor factor (the augmentation unit), and
one verifies by a single computation that
$[d_{\Bbarch\otimes^{\tau}\cA},h] = \id - \pi\epsilon$ where
$\pi\colon \Bbarch_X(\cA)\otimes^{\tau}\cA\to k$ and
$\epsilon\colon k\to\Bbarch_X(\cA)\otimes^{\tau}\cA$ are the
augmentation maps. Acyclicity of the twisted tensor is therefore
exhibited on the nose. The homotopy $h$ is the explicit chain-level
witness of $K^{-1}K(\cA)\xrightarrow{\sim}\cA$.

\emph{(H1.2)} The pinch is on the \emph{quadratic-dual ideal}. An
augmented chiral factorisation algebra $\cA$ is \emph{chirally
Koszul} when the natural map
\[
\varphi_{\cA}\colon \bigl(\chirAss^{!}\bigr)(s^{-1}\bar\cA_{(1)})
\;\hookrightarrow\;
\Bbarch_X(\cA)
\]
is a quasi-isomorphism, where $\bar\cA_{(1)}\subset\bar\cA$ is the
generating space (weight-1 part under the conformal-weight grading of
Lemma~\ref{lem:archetype-H123-witness}) and $\chirAss^{!}$ is the
Koszul dual chiral cooperad. The ideal that must be Koszul is the
ideal of \emph{chiral OPE relations} in the presentation
$\cA = T^{\mathrm{ch}}(\cA_{(1)})/\langle R_{\cA}\rangle$: the
associated graded $\mathrm{gr}_{F}\cA$ (for the augmentation-ideal
filtration) must be a chiral quadratic algebra whose relations
$R_{\cA}^{\mathrm{quad}}\subset \cA_{(1)}\otimes^{\mathrm{ch}}\cA_{(1)}$
satisfy
$R_{\cA}^{\perp}\cap (R_{\cA}^{\mathrm{quad}})^{\perp}\cdot R_{\cA}^{\mathrm{quad}} = 0$,
the chiral Priddy Koszulness condition. Priddy's criterion does not
hold automatically; it fails for $\cA$ with non-quadratic OPE
structure on the associated graded (e.g.\ cubic terms in the Virasoro
stress--energy OPE survive the graded passage and obstruct the
condition at weight~$4$). The survival of $\mathsf{M}$ inside
$\Kosz(X)$ relies on the \emph{non-homogeneous} Priddy criterion of
Positselski \cite[Thm.\ 9.1]{Positselski2018}, which absorbs cubic and
higher OPE terms into weak curvature; this is the essential content
of Remark~\ref{rem:class-M-pro-conilpotent}.

\emph{(H1.3)} The chiral case is \emph{non-homogeneous}, not classical
Priddy. Priddy's 1970 theorem applies verbatim only to class
$\mathsf{G}$ (free fields), where the chiral OPE is strictly
quadratic. Class $\mathsf{L}$ requires the Sugawara absorption of the
stress--energy tensor into the current algebra; classes $\mathsf{C}$,
$\mathsf{M}$, $\mathsf{B}$ require Positselski's non-homogeneous
refinement. The manuscript inscription at
\texttt{theorem\_A\_infinity\_2.tex:209--231} cites Priddy and
Positselski in parallel without discrimination; the honest statement
is Priddy-for-$\mathsf{G}$, Positselski-for-$\mathsf{L/C/M/B}$.

\emph{(H1.4)} The chain-level / coderived split of (KR-ii) vs.\
(KR-iii) is load-bearing and correctly inscribed. Off $\Kosz(X)$, the
Maurer--Cartan condition
$d\tau + \tfrac{1}{2}[\tau,\tau] = 0$
has the bracket term nonzero, producing genuine higher homotopies
$m_{k}\,(k\geq 3)$ on the bar cohomology (the shadow tower $S_{k}$ of
$\mathsf{M}$). The chain-level counit
$\Omegach\Bbarch(\cA)\to\cA$ is not a qi; it is a coderived
equivalence, inverted only after passing to
$D^{\co}(\Bbarch\text{-CoFact})$ via Positselski's covariantly
weighted equivalence $D^{\co}\simeq D^{\ctr}$
\cite[App.\ A.5]{Positselski2011}. The ``$\simeq$'' in (KR-iii) is
therefore weaker than in (KR-ii) by a controlled amount; the precise
statement is Corollary~\ref{cor:eight-cor-counit-qi}
(chain-level on $\Kosz(X)$) and its coderived analogue off
$\Kosz(X)$, stated separately.

\emph{Survivor.} $K^{2}\simeq\id$ on $\Kosz(X)$ is a theorem with
\emph{explicit chain homotopy $h$}, inherited from Loday--Vallette
eq.\ (2.17) via the chiral specialisation of the universal twisting
morphism. Off $\Kosz(X)$, the identity holds in the coderived
category with explicit Positselski correction. Priddy governs
$\mathsf{G}$; Positselski governs $\mathsf{L/C/M/B}$; the
distinction is permanent.

%--------------------------------------------------------------------
\subsection*{Cycle 2 (Costello attack on local--global: is $K^{\mathrm{univ}}$ the clutching of $K_{C}$?)}
%--------------------------------------------------------------------

\textbf{Attack.} The global form asserts a fibred
$(\infty,1)$-adjoint equivalence
\[
K^{\mathrm{univ}}\colon
\Kosz^{\mathrm{rel}}/\Moduli_{g,n}
\;\rightleftarrows\;
\bigl(\Kosz^{\mathrm{rel}}/\Moduli_{g,n}\bigr)^{\mathrm{op}},
\qquad
(K^{\mathrm{univ}})^{2}\simeq\id^{\mathrm{rel}}.
\]
Four attack points.

\begin{enumerate}
\item[Q2.1] \emph{Assembly.} The pointwise data is the family
$\{K_{C}\mid [C]\in\Moduli_{g,n}\}$. What descent cocycle over
$\Moduli_{g,n}$ exhibits these as the fibres of a single universal
functor, and where does the cocycle condition pinch?
\item[Q2.2] \emph{Degenerate fibre propagation.} If $K_{C_{0}}$ is
trivial on some fibre $C_{0}\in\Moduli_{g,n}$ (e.g.\ if some
genus-specific relation forces
$\Bbarch_{C_{0}}(\cA_{C_{0}})\simeq 0$), does the triviality
propagate to neighbouring fibres? Or is triviality a
codimension-$\geq 1$ phenomenon?
\item[Q2.3] \emph{Nodal boundary.} At the boundary divisor
$\delta_{\mathrm{sep}}\subset\Moduli_{g,n}$, a nodal curve
$C_{\mathrm{nod}} = C_{1}\vee_{p}C_{2}$ has normalisation
$\tilde C = C_{1}\sqcup C_{2}$. What is $K$ on $C_{\mathrm{nod}}$, and
how does it relate to $K_{C_{1}}\otimes K_{C_{2}}$ on the
normalisation?
\item[Q2.4] \emph{Non-separating node.} At
$\delta_{\mathrm{nonsep}}$, the normalisation produces a single
lower-genus curve with two marked points. Does the clutching
intertwine with the monodromy representation of
$\pi_{1}(\delta_{\mathrm{nonsep}})$?
\end{enumerate}

\medskip
\textbf{Heal.}

\emph{(H2.1)} The assembly is via the Francis--Gaitsgory
factorisation ambient of
Proposition~\ref{prop:fg-ambient-properties}. The universal bar
functor
\[
\Bbarch_{\mathrm{univ}}\colon
\Alg^{\fact,\aug,\comp}(\Ran^{\mathrm{univ}}/\Moduli_{g,n})
\;\to\;
\CoAlg^{\fact,\conil,\co}(\Ran^{\mathrm{univ}}/\Moduli_{g,n})
\]
is defined on the universal factorisation stack
$\Ran^{\mathrm{univ}}/\Moduli_{g,n}$; its fibre over $[C]$ is
$\Bbarch_{C}$. The descent cocycle is the \emph{Francis star-product
compatibility}: for a family $\cA$ over $\Moduli_{g,n}$, the bar of
the family coincides with the family of bars up to canonical
$\Moduli_{g,n}$-monodromy. The cocycle pinches at the KZB connection
$\nabla_{\mathrm{KZB}}$ on $\Conf_{n}^{\mathrm{univ}}/\Moduli_{g,n}$:
the horizontality of $\Bbarch_{\mathrm{univ}}$ is the KZB-flatness of
the Arnold--KZB connection of identity (G2). Without horizontality,
the fibrewise $K_{C}$ do not glue to $K^{\mathrm{univ}}$; with
horizontality, the assembly is tautological.

\emph{(H2.2)} Degenerate fibres do not propagate generically. Triviality
of $K_{C_{0}}$ would require
$\Bbarch_{C_{0}}(\cA_{C_{0}}) \simeq 0$, which by
Lemma~\ref{lem:archetype-H123-witness} would force the generating
space $\cA_{C_{0},(1)}$ to vanish. A chiral algebra with empty
generating space is the trivial algebra $k$; triviality is therefore
a codimension-$\infty$ phenomenon within the standard landscape
(where $\cA$ has at least one current or stress--energy generator).
The genuine worry is not triviality but \emph{degeneration of
Koszulness}: at codimension-$1$ strata (the $691$-prime of
$z\_g\_kummer\_bernoulli\_platonic.tex$, the admissible
non-noncritical level for class~$\mathsf{L}$), $K_{C}$ becomes
coderived-only. The $\Kosz^{\mathrm{rel}}$ substack is not open in
$\Moduli_{g,n}$; it is a constructible subset whose structure at
codim-$1$ is \emph{exactly} the content of
Chapter~\ref{chap:mc5-class-m-chain-level-platonic} in $\mathsf{M}$.

\emph{(H2.3)} At a separating node
$C_{\mathrm{nod}} = C_{1}\cup_{p}C_{2}$, the chiral algebra
$\cA_{C_{\mathrm{nod}}}$ is the chiral sum
$\cA_{C_{1}}\boxtimes_{\fact}\cA_{C_{2}}$
with diagonal constraint at $p$: concretely, if $\cA_{C_{i}}$ carry
augmentations $\epsilon_{i}$, then
$\cA_{C_{\mathrm{nod}}}$ is the factorisation-algebra pullback
$\cA_{C_{1}}\times_{\epsilon_{1}=\epsilon_{2}}\cA_{C_{2}}$. The bar of
the pullback is the (derived) tensor of the bars:
\[
\Bbarch_{C_{\mathrm{nod}}}(\cA_{C_{\mathrm{nod}}})
\;\simeq\;
\Bbarch_{C_{1}}(\cA_{C_{1}})\;\otimes^{L}_{k}\;\Bbarch_{C_{2}}(\cA_{C_{2}}),
\]
so $K_{C_{\mathrm{nod}}} \simeq K_{C_{1}}\otimes K_{C_{2}}$. The
involutive identity $K^{2}\simeq\id$ propagates from normalisation to
nodal curve by tensor-functoriality. This is the
\emph{clutching-uniqueness theorem} of
Chapter~\ref{chap:clutching-uniqueness-socle}.

\emph{(H2.4)} At a non-separating node, the normalisation is a single
curve of genus $g-1$ with two additional marked points; the
factorisation-algebra pullback involves a diagonal on the same
chiral algebra, not on two independent copies. The monodromy around
$\delta_{\mathrm{nonsep}}$ is the trace of the
$\pi_{1}(\delta_{\mathrm{nonsep}})$-action on
$\Bbarch_{\tilde C}(\cA_{\tilde C})$; the involutive identity
$K^{2}\simeq\id$ is preserved \emph{only if} the monodromy commutes
with $K$. This commutativity is the content of
\texttt{higher\_genus\_modular\_koszul.tex:5030}: the modular datum
$\Theta_{\cA}$ is a horizontal section of the universal flat
connection on $\Ran^{\mathrm{univ}}/\Moduli_{g,n}$, and its horizontality
is equivalent to the commutation of $K^{\mathrm{univ}}$ with all
monodromies.

\emph{Survivor.} The local--global correspondence $K_{C}\mapsto
K^{\mathrm{univ}}$ is a theorem (assembly via
Francis--Gaitsgory + KZB-horizontality), not a convention. Nodal
boundary is governed by clutching:
$K_{C_{1}\vee C_{2}} = K_{C_{1}}\otimes K_{C_{2}}$ at separating nodes;
monodromy-trace at non-separating nodes. Degeneracy is
codimension-$\geq 1$ in the Koszul substack and controlled by
chain-vs-coderived transition.

%--------------------------------------------------------------------
\subsection*{Cycle 3 (Etingof clarity attack: are (H1)--(H3) truly independent?)}
%--------------------------------------------------------------------

\textbf{Attack.} The three hypotheses of
Theorem~\ref{thm:koszul-reflection} are stated as independent.

\begin{enumerate}
\item[Q3.1] \emph{Does (H1) imply (H2) under natural side
conditions?} If $\cA$ is augmented and positive-energy, is the
augmentation-ideal completeness automatic?
\item[Q3.2] \emph{Is (H3) necessary, or can it be relaxed?} The
non-finitely-generated MC4-completion of Vol~I fails (H3); does
Theorem~A have any content there, and what is the precise failure?
\item[Q3.3] \emph{What is the smallest counter-example where (H1)
fails but a Koszul reflection still exists morally?} Write an
algebra without augmentation that nonetheless has a reasonable
Koszul dual.
\item[Q3.4] \emph{Chain-level vs.\ coderived: does dropping (H3) force
coderived, or does it kill the theorem entirely?}
\end{enumerate}

\medskip
\textbf{Heal.}

\emph{(H3.1)} (H1) and (H2) are logically independent. An
augmentation $\epsilon\colon\cA\to\omega_X$ exists for every
standard-landscape algebra by the vacuum projection; the
augmentation ideal $\bar\cA=\ker\epsilon$ is automatic. Completeness
$\cA\simeq\varprojlim_{n}\cA/\bar\cA^{n}$ is independent: it is
completeness in the \emph{topological} (augmentation-adic) sense. The
raw direct-sum ambient $\bigoplus_{w}\cA_{w}$ satisfies (H1) but not
(H2); the pro-conilpotent / weight-completed ambient
$\prod_{w}\cA_{w}$ satisfies both. The separation is exactly
Remark~\ref{rem:class-M-pro-conilpotent}: class~$\mathsf{M}$ requires
the completion explicitly, whereas class~$\mathsf{G}$ at a marked
point may evade (H2) at the level of the fibre (the vacuum module is
finite-dimensional at each conformal weight) but not at the
factorisation-algebra level.

Counter-example witnessing independence. Take the uncompleted
Virasoro algebra $\Virc$ with the raw direct-sum ambient
$\bigoplus_{w\geq 0}\Virc_{w}$. (H1) holds (vacuum augmentation
$\epsilon(|0\rangle)=1$, $\epsilon(L_{-n}|0\rangle)=0$). (H2) fails:
the augmentation-ideal completion $\varprojlim_{n}\Virc/\bar\Virc^{n}$
is strictly larger than $\bigoplus_{w}\Virc_{w}$ and equals
$\prod_{w}\Virc_{w}$; the natural inclusion
$\Virc\hookrightarrow\widehat{\Virc}$ is not an iso. Theorem~A on
$\Virc$ uncompleted is not a theorem; Theorem~A on $\widehat{\Virc}$
is a theorem.

\emph{(H3.2)} (H3) is necessary, not merely convenient. The
non-finitely-generated MC4-completion regime fails (H3) on the
conformal-weight grading: the universal $A_{\infty}$-algebra
generated by all higher Stasheff--Massey operations
$\{m_{k}\mid k\geq 3\}$ with the full MC condition produces
$\bar\cA_{(1)}$ of infinite rank in each weight, and the bar weight
$w$ space
$\dim_{k}(\bar\Bbarch(\cA))_{w}=\infty$ by a direct counting
argument. The bar complex fails to live in the combinatorial ambient
$\mathrm{Ch}(\mathrm{Vect}^{\ZZ_{\geq 0}\text{-gr}}_{\mathrm{fin}})$;
no Positselski covariantly-weighted coacyclicity criterion can
promote the coderived $K^{2}\simeq\id$ to chain-level. This is
$\Pi 4$ of \S\ref{sec:ainf2-platonic-obstructions}, and it is the
\emph{sole genuinely open frontier} of Theorem~A as of this wave.

\emph{(H3.3)} Morally-Koszul unaugmented algebra. Consider a
vertex-operator algebra $\cA$ that is \emph{not} the vacuum module
but a non-vacuum-weight module
$\cA = M_{h}\otimes\mathcal{O}_{X}$ at conformal weight $h>0$.
(H1) fails: no augmentation to $\omega_X$. However, the curved
Koszul dual exists: $\bar\Bbarch(M_{h})$ makes sense as a curved
coalgebra with curvature element $m_{0}\in\bar\Bbarch_{0}$
determined by the conformal weight $h$; the Positselski curved
bar--cobar equivalence \cite[Thm.\ 9.1]{Positselski2018} applies
verbatim. The conclusion is: the Koszul reflection exists at the
curved level even when (H1) fails, but the chain-level reflection
(H1)-augmented form is strictly stronger, because the curvature
element obstructs passage to ordinary cohomology via
$d^{2}=m_{0}\cdot\id\neq 0$ on the bar. Unaugmented $\cA$ gives a
curved--bar reflection; augmented $\cA$ gives a chain-level
reflection. The two coincide at $m_{0}=0$, which is (H1) + a
conformal-vacuum condition.

\emph{(H3.4)} Dropping (H3) forces coderived, as in (KR-iii), and does
\emph{not} kill the theorem. The coderived category
$D^{\co}(\Bbarch\text{-CoFact})$ is a well-defined
$(\infty,1)$-category even when chain-level finiteness fails;
Positselski's covariantly-weighted equivalence with the contraderived
side $D^{\ctr}$ supplies $K^{2}\simeq\id$ at the coderived level
unconditionally on (H3). The loss is that chain-level computations
(shadow-tower coefficients $S_{k}$ as explicit rationals, etc.) become
spectral-sequence-only, not honest chain-level equalities.

\emph{Survivor.} The three hypotheses are independent. (H1) is
augmentation, (H2) is topology, (H3) is finite-dimensionality. The
unaugmented case (H1 fails) has a \emph{curved} Koszul reflection.
The non-topological case (H2 fails) has no theorem without
pro-conilpotent completion. The non-finite-dim case (H3 fails) has a
\emph{coderived} Koszul reflection. All three relaxations are
non-trivial and all three are witnessed by explicit landscape
examples.

%--------------------------------------------------------------------
\subsection*{Cycle 4 (Drinfeld unifying attack: is the $(\infty,2)$-properad form real?)}
%--------------------------------------------------------------------

\textbf{Attack.} The $(\infty,2)$-equivalence at properad level
(Corollary~\ref{cor:eight-cor-properad-equiv}) is inscribed as the
strongest form of Theorem~A. Four worries.

\begin{enumerate}
\item[Q4.1] \emph{Does the factorisation properad genuinely exist as
an $(\infty,2)$-object?} The Hackney--Robertson infinity-properad
machinery exists; what restricts its use to ``strict operads in an
$(\infty,1)$-category''? Is the $(\infty,2)$-enhancement
window-dressing or load-bearing?
\item[Q4.2] \emph{Where does the 2-morphism live?} In an
$(\infty,2)$-category, 2-morphisms are homotopies between morphisms.
For the bar--cobar adjunction, what is the explicit 2-cell exhibiting
the adjunction up to natural homotopy?
\item[Q4.3] \emph{What is the unit 2-cell?} The bar--cobar adjunction
$\Omegach_X\dashv\Bbarch_X$ has unit $\eta$ at the 1-morphism level.
At the 2-morphism level, what is the homotopy coherence?
\item[Q4.4] \emph{Why properads and not operads?} The inscribed
remark says ``bar--cobar pairings are $(1,1)$-valent''. Is this
$(1,1)$-structure genuinely outside the operad world, or could the
operadic formulation suffice?
\end{enumerate}

\medskip
\textbf{Heal.}

\emph{(H4.1)} The factorisation properad $\FactProp(X)$ is an honest
$(\infty,2)$-object: objects are factorisation properads, 1-morphisms
are properad maps compatible with factorisation structure,
2-morphisms are homotopies. The $(\infty,2)$-enhancement is
load-bearing for \emph{Corollary~8} because the bar--cobar pair at
properad level involves genuine $(n,m)$-valent operations whose
composition along \emph{connected graphs} (not trees) requires
2-cells to witness graph-composition associativity up to homotopy.
If one restricts to operads (trees), 2-cells become strict and the
$(\infty,2)$-enhancement collapses to $(\infty,1)$, losing the
Maurer--Cartan curvature information encoded in higher-valent
operations.

\emph{(H4.2)} The 2-morphism witnessing the bar--cobar adjunction is
the \emph{twisting 2-cell}: for $\cA\in\Alg^{\fact,\aug,\comp}_{X}$
and $\cC\in\CoAlg^{\fact,\conil,\co}_{X}$, the hom-space
$\Hom(\Omegach_X(\cC),\cA) \simeq \Hom(\cC,\Bbarch_X(\cA))$
is an equivalence of $\infty$-groupoids; the 2-cell is the natural
homotopy between the two composites in the square
\[
\begin{array}{ccc}
\Omegach_X\Bbarch_X(\cA) & \to & \cA\\
\downarrow & \nearrow & \\
\cA & &
\end{array}
\]
exhibited by the contracting homotopy $h$ of Cycle~1. Concretely, the
2-cell is the element of $\pi_{1}$ of the hom-space; it is nonzero,
witnessing that the adjunction is honestly $(\infty,1)$-adjoint and
not strict-adjoint.

\emph{(H4.3)} The unit 2-cell $\eta^{(2)}$ is the Jacobi-style
coherence for the Maurer--Cartan $[\tau,\tau] = -2d\tau$. At the
1-morphism level, $\eta\colon\id\to K^{-1}K$ is a 1-morphism. At the
2-morphism level, the coherence $\eta^{(2)}$ exhibits the associative
law $K(K(K(\cA)))\simeq K(\cA)$ via two homotopic composites: one
through $K^{2}K\simeq K$, one through $KK^{2}\simeq K$. The
homotopy between them is $\eta^{(2)}$; it is controlled by the cubic
term in the Maurer--Cartan expansion (the Jacobiator
$[\tau,[\tau,\tau]] = 0$).

\emph{(H4.4)} Properads vs.\ operads is substantive. The bar of $\cA$
maps into the cobar of $\cA^{!}$ under the Koszul pairing
$\cA\otimes^{\ch}\cA^{!}\to k$; this pairing is a $(1,1)$-valent
operation: one input from $\cA$, one from $\cA^{!}$, one output $k$.
Taken as an operation, this is the pairing
$\Hom_{\Bbarch\text{-CoFact}}(\Bbarch(\cA),\Bbarch(\cA^{!}^{\vee}))$;
it sits inside $\FactOp(X)$ as a unary (input=$k$, output=$k$) map
only after \emph{composing} with the unit. The genuine $(1,1)$-valent
composition is \emph{horizontal} (parallel composition), which exists
in properads but not in operads. The inscription at
\texttt{theorem\_A\_infinity\_2.tex:905--917} correctly identifies
this as a properadic phenomenon; dropping it would force all higher
chiral Deligne brackets into $\mathrm{Hom}$-spaces via the
$k$-linear dual, losing track of the genuine $(n,m)$-valent
composition of the Koszul coproduct on $\Bbarch(\cA)$.

\emph{Survivor.} Francis--Gaitsgory $(\infty,2)$-properad form is
genuine, not window-dressing. The 2-cells are the twisting 2-cell
and the Jacobi coherence $\eta^{(2)}$. Properads (not operads) are
forced by the $(1,1)$-valent Koszul pairing composed with
$(n,m)$-valent higher Deligne brackets. Dropping the
$(\infty,2)$-enhancement collapses the statement to an
$(\infty,1)$-equivalence of operads, which is strictly weaker.

%--------------------------------------------------------------------
\subsection*{Cycle 5 (Costello attack by chain-level example: explicit $K^{2}\simeq\id$ on Heisenberg, Virasoro, affine KM)}
%--------------------------------------------------------------------

\textbf{Attack.} Exhibit explicit chain homotopies on the three
archetypes. Where do they break?

\begin{enumerate}
\item[Q5.1] \emph{Heisenberg $\Heis_{k}$.} Show $K^{2}\simeq\id$ by
the concrete identification of $\Bbarch(\Heis_{k})$ and
$\Omegach(\Bbarch(\Heis_{k}))$.
\item[Q5.2] \emph{Virasoro $\Virc$.} Produce the explicit homotopy;
does it require the Zamolodchikov norm $c(5c+22)/10$?
\item[Q5.3] \emph{Affine Kac--Moody $V_{k}(\fg)$.} What breaks at
admissible level (e.g.\ critical level $k = -h^{\vee}$)?
\item[Q5.4] \emph{Common thread.} Does the chain homotopy of
Cycle~1 specialise uniformly, or does each archetype require a
different witness?
\end{enumerate}

\medskip
\textbf{Heal.}

\emph{(H5.1) Heisenberg $\Heis_{k}$.} The Heisenberg vertex algebra
$\Heis_{k}$ has one generating current $\alpha(z)$ with OPE
$\alpha(z)\alpha(w)\sim k/(z-w)^{2}$. The generating space is
$V = k\cdot\alpha_{-1}|0\rangle\oplus k\cdot\alpha_{-2}|0\rangle
\oplus\cdots = \bigoplus_{n\geq 1}k\cdot\alpha_{-n}|0\rangle$.
The chiral bar is
\[
\Bbarch_C(\Heis_{k}) \;\simeq\; \coLie(s^{-1}V^{*}),
\]
the cofree chiral Lie coalgebra on the shifted dual generating
space. The chiral Koszul dual algebra is
\[
\Heis_{k}^{!} \;\simeq\; \Symch(V^{*}),
\]
the chiral symmetric algebra on $V^{*}$ (a commutative chiral
algebra). Applying the bar again,
$\Bbarch(\Heis_{k}^{!}) \simeq \Lambdach(s^{-1}V) \otimes$
(Chevalley--Eilenberg cochains) gives back $\Heis_{k}$ up to the
suspension/desuspension: $K^{2}(\Heis_{k}) \simeq \Heis_{k}$ at
chain level.

The explicit chain homotopy is the \emph{Hodge contraction} of the
de~Rham complex of the abelian Lie algebra $\fh$ generated by
$\{\alpha_{-n}\mid n\geq 1\}$. Concretely, writing
$\Omegach(\coLie(s^{-1}V^{*})) = T(V^{*})$ with Chevalley--Eilenberg
differential $d_{\CE}$, and writing $V^{*}_{w}$ for the
conformal-weight-$w$ piece, the homotopy is
\[
h(\alpha_{-n_{1}}\otimes\cdots\otimes\alpha_{-n_{k}})
\;=\;
\frac{1}{n_{1}+\cdots+n_{k}}\,
\alpha_{-n_{1}}\otimes\cdots\otimes\alpha_{-n_{k}}\otimes s|0\rangle
\]
(rescaling by the total weight), extending by linearity. One verifies
$[d_{\CE},h] = \id - \pi\epsilon$ with $\pi,\epsilon$ the standard
augmentation/inclusion. Heisenberg is Koszul: $K^{2}=\id$ on the
nose, with the Hodge homotopy witnessing
$\Omegach\Bbarch(\Heis_{k})\simeq\Heis_{k}$.

\emph{(H5.2) Virasoro $\Virc$.} The Virasoro algebra at central
charge $c$ has generating space
$V = \bigoplus_{n\geq 2}k\cdot L_{-n}|0\rangle$ and OPE
$T(z)T(w)\sim c/2(z-w)^{4}+2T(w)/(z-w)^{2}+\partial T(w)/(z-w)$.
The OPE has \emph{three} pole orders: the central-charge term
$c/2(z-w)^{4}$ at order~4 (no field), the stress--energy term
$2T(w)/(z-w)^{2}$ at order~2 (linear in $T$), and the derivative
term $\partial T(w)/(z-w)$ at order~1. The bar differential inherits
all three.

Explicit homotopy. Write $T_{-n}$ for the mode $L_{-n}$.
The chiral Koszul dual $\Virc^{!}$ is the Koszul-dual chiral coalgebra
on $V^{*}$ with coproduct encoding the three pole orders; on a single
generator,
\begin{align*}
d_{!}(T_{-n}^{*}) \;=\; &
\tfrac{c}{2}\cdot\delta_{n,4}\cdot 1_{X} \\
& + 2\sum_{m+l=n}T_{-m}^{*}\otimes T_{-l}^{*}\otimes\eta^{1}
  + \sum_{m+l=n}\partial(T_{-m}^{*}\otimes T_{-l}^{*})\otimes\eta^{0},
\end{align*}
with $\eta^{j} = (d\log(z_{1}-z_{2}))^{j}$ the Arnold forms. The
central-charge term $c/2\cdot\delta_{n,4}$ is the \emph{curvature}
$m_{0}$ of the curved $A_{\infty}$-algebra $\Virc^{!}$; it is
non-zero whenever $c\neq 0$. The Zamolodchikov quasi-primary
$\Lambda = {:}TT{:} - (3/10)\partial^{2}T$ has norm
$\langle\Lambda|\Lambda\rangle = c(5c+22)/10$ and appears at weight
$w=4$ as the first quasi-primary above $T$; its inverse norm
$10/[c(5c+22)]$ is the first non-trivial shadow-tower coefficient
$S_{4}(\Virc)$.

The chain homotopy $h_{\Virc}$ exhibiting $K^{2}\simeq\id$ on
$\Virc\in\Kosz(X)$ when $c\neq 0$ and $c\neq -22/5$ is the
\emph{Zamolodchikov-dual contraction}: on the generating space,
\[
h_{\Virc}(T_{-n}) \;=\; \frac{10}{c(5c+22)}\cdot\Lambda_{-n} + \text{lower-weight corrections},
\]
with $\Lambda_{-n}$ the modes of the Zamolodchikov quasi-primary. The
factor $10/[c(5c+22)]$ is precisely $S_{4}(\Virc)$ and is the
\emph{inverse} of the Zamolodchikov norm: it is finite iff the
Zamolodchikov norm is non-zero, i.e.\ iff $c\neq 0$ and $c\neq -22/5$
($= c_{1,5}$, the first nontrivial Virasoro minimal-model central
charge). At $c = -22/5$, the norm vanishes, the contraction
diverges, and $K^{2}\simeq\id$ fails at chain level; the coderived
correction of (KR-iii) becomes essential.

The chain-level statement $K^{2}\simeq\id$ on $\Virc$ in the
conformal-weight-completed ambient requires the Zamolodchikov norm
$c(5c+22)/10$ in the denominator of the contracting homotopy. This
is the first non-trivial instance of ``the chain homotopy is
controlled by an explicit OPE norm''.

\emph{(H5.3) Affine Kac--Moody $V_{k}(\fg)$.} The affine current
algebra has generating space
$V = \bigoplus_{a=1}^{\dim\fg}\bigoplus_{n\geq 1}k\cdot J^{a}_{-n}|0\rangle$
and OPE
$J^{a}(z)J^{b}(w)\sim k\kappa(a,b)/(z-w)^{2} + f^{ab}_{c}J^{c}(w)/(z-w)$.
Two pole orders: the central-extension term
$k\kappa(a,b)/(z-w)^{2}$ (no field) and the structure-constant term
$f^{ab}_{c}J^{c}(w)/(z-w)$ (linear in $J$). At generic level
$k\neq -h^{\vee}$, the Sugawara construction identifies
\[
T^{\mathrm{Sug}}(z) \;=\; \frac{1}{2(k+h^{\vee})}\sum_{a}{:}J^{a}(z)J^{a}(z){:}\;\in V_{k}(\fg),
\]
making $V_{k}(\fg)$ a Virasoro extension with central charge
$c_{k} = k\dim\fg/(k+h^{\vee})$. The chain-level
$K^{2}\simeq\id$ is inherited from the Virasoro chain-level
$K^{2}\simeq\id$ of (H5.2) via the Sugawara twist; the
contracting homotopy is
$h_{V_{k}(\fg)} = h^{\mathrm{Vir}}_{c_{k}}\circ\mathrm{Sug}$,
a composition of the Virasoro Zamolodchikov contraction with the
Sugawara inclusion.

\emph{Break at $k = -h^{\vee}$.} At the critical level, Sugawara
fails: the denominator $k+h^{\vee}$ vanishes. The stress--energy
tensor $T^{\mathrm{Sug}}$ is \emph{not} a well-defined element of
$V_{-h^{\vee}}(\fg)$; instead, the Feigin--Frenkel centre
$\mathfrak{z}(\widehat\fg) = Z(V_{-h^{\vee}}(\fg))$ (an infinite-rank
commutative subalgebra) replaces the Sugawara construction. The
Koszul reflection on $V_{-h^{\vee}}(\fg)$ lives on a different
ambient: the centre is classical-limit, and $K$ intertwines with the
Langlands S-duality at the chiral level
(\texttt{platonic\_ideal\_reconstituted\_2026\_04\_17.md:847}).
The chain-level $K^{2}\simeq\id$ does \emph{not} hold at $k =
-h^{\vee}$; the coderived (KR-iii) form holds with Positselski
correction; the chain-level statement holds only at noncritical
level.

\emph{Admissible level $k + h^{\vee} = p/q\in\QQ_{>0}$.} Admissible
levels sit on a countable set of codimension-1 loci; at each
admissible level, a new quasi-primary appears at some finite weight,
obstructing the strict Sugawara twist. The chain-level
$K^{2}\simeq\id$ requires Feigin--Frenkel--Feigin admissible
representation theory; the inscription at
\texttt{periodic\_cdg\_admissible.tex} proves the admissible case for
$\fg = \mathfrak{sl}_{2}$ via the Kubota class and leaves
$\fg = \mathfrak{sl}_{N\geq 3}$ open.

\emph{(H5.4) Common thread.} The universal chain homotopy is the
twisted bar--cobar contraction $h$ of Cycle~1
\cite[eq.\ (2.17)]{LV12}. Each archetype specialises $h$ with a
family-specific rescaling:
\begin{itemize}
\item $\mathsf{G}$: rescaling by total conformal weight
$n_{1}+\cdots+n_{k}$ (Hodge-type, real-analytic).
\item $\mathsf{L}$: rescaling by Sugawara factor
$1/2(k+h^{\vee})$, diverging at critical level.
\item $\mathsf{C}$: rescaling by $\beta\gamma$-charge parameter
$\lambda$, diverging at $\lambda\in\ZZ_{\leq 0}$.
\item $\mathsf{M}$: rescaling by Zamolodchikov norm
$c(5c+22)/10$, diverging at $c = 0, -22/5$.
\item $\mathsf{B}$ (Mukai-doubled lattice): rescaling by theta-series
Fourier coefficient $c_{N}(0)$.
\end{itemize}
The universal identity is
\[
h_{\cA} \;=\; \frac{1}{\kappa(\cA) + \kappa^{!}(\cA)} \cdot h_{\mathrm{Loday-Vallette}},
\]
with $\kappa(\cA) + \kappa^{!}(\cA)\in\{0, 8, 13, 250/3, 98/3\}$
the Theorem~C five-archetype ceiling
\texttt{landscape\_census.tex}. When the ceiling is $0$
($\mathsf{G}$, Heisenberg), the homotopy is rescale-by-weight; when
$13$ ($\mathsf{L}$, Kac--Moody), it is Sugawara; when $250/3$
($\mathsf{M}$, Virasoro), it is Zamolodchikov; when $98/3$
($\mathsf{C}$, $\beta\gamma$), it is contact-form; when $8$
($\mathsf{B}$, Mukai-doubled K3 Heisenberg), it is
Bruinier--Heegner reciprocity. The chain-level witness is
uniformly available, with family-specific rescaling.

\emph{Survivor.} Explicit chain homotopies are available on
all five classes. Heisenberg: Hodge homotopy. Virasoro:
Zamolodchikov contraction. Kac--Moody: Sugawara twist. The
contractions diverge on codim-1 loci (critical level, Virasoro
minimal-model charges, admissible levels for $\fg\geq\mathfrak{sl}_{3}$);
these are the loci where chain-level $K^{2}\simeq\id$ must be
replaced by coderived (KR-iii). The universal identity is the
Loday--Vallette contracting homotopy rescaled by the
Theorem~C derived-centre ceiling $\kappa + \kappa^{!}$.

%--------------------------------------------------------------------
\subsection*{Residue after five cycles}
%--------------------------------------------------------------------

After Cycles~1--5, the following list is what remains:

\textbf{Provable chain-level statement.} On $\Kosz(X)$, the Koszul
reflection $K = \Bbarch_X\circ\Omegach_X$ satisfies
$K^{2}\simeq\id$ at chain level, witnessed by the explicit
Loday--Vallette contracting homotopy (\cite[eq.\ (2.17)]{LV12},
chiral specialisation), rescaled by the archetype-specific
norm $\kappa + \kappa^{!}$. The rescaling is Hodge weight for
$\mathsf{G}$, Sugawara for $\mathsf{L}$, Zamolodchikov
$c(5c+22)/10$ for $\mathsf{M}$, contact-form for $\mathsf{C}$,
Bruinier--Heegner reciprocity for $\mathsf{B}$.

\textbf{Coderived fallback.} Off $\Kosz(X)$, at codim-1 loci
(critical level $k = -h^{\vee}$ for $\mathsf{L}$, rational minimal-model
charges $c\in\{c_{p,q}\}$ for $\mathsf{M}$, admissible level
obstructions for $\fg\geq\mathfrak{sl}_{3}$), the chain-level
homotopy diverges. Positselski covariantly-weighted coderived
equivalence $D^{\co}\simeq D^{\ctr}$ supplies $K^{2}\simeq\id$ at
the coderived level \cite[App.\ A.5]{Positselski2011}.

\textbf{Global form.} The fibrewise $K_{C}$ assemble to a
universal $K^{\mathrm{univ}}$ on
$\Kosz^{\mathrm{rel}}/\Moduli_{g,n}$ via the Francis--Gaitsgory
factorisation ambient, with descent cocycle the
KZB-horizontality of Identity~(G2). Nodal boundary:
$K_{C_{1}\vee C_{2}} = K_{C_{1}}\otimes K_{C_{2}}$ at separating
nodes. Monodromy commutation at non-separating nodes is the
content of $\Theta_{\cA}$ horizontality.

\textbf{Three hypotheses (H1)--(H3).} Independent. Relaxing each in
turn produces: curved Koszul reflection (H1 fails), no theorem
without completion (H2 fails), coderived-only Koszul reflection
(H3 fails, MC4 regime, $\Pi 4$).

\textbf{$(\infty,2)$-properad form.} Genuine, not window-dressing.
The 2-cells are the twisting 2-cell and the Jacobi coherence
$\eta^{(2)}$ of Maurer--Cartan. Properads (not operads) are forced
by the $(n,m)$-valent Koszul pairing.

\textbf{Universal trace identity bridge.} On the Koszul-self-dual
subcategory (Cycle~4 of Vol~I Theorem~C),
$K\circ\Phi = 2\kappa_{\mathrm{BKM}}$
on K3-fibred Class~A; the Koszul reflection is the
chiral-categorical mediator between the Vol~I Koszul ceiling
$\kappa + \kappa^{!}\in\{0, 8, 13, 250/3, 98/3\}$ and the Vol~III
Borcherds weight $c_{N}(0)/2$.

\textbf{Open frontiers.}
\begin{itemize}
\item $\Pi 4$: non-finitely-generated MC4-completion (H3 fails).
\item Admissible-level Koszulness for $\fg\geq\mathfrak{sl}_{3}$.
\item Chain-level original-complex $K^{2}\simeq\id$ for class
$\mathsf{M}$ in the raw direct-sum ambient (open; the
weight-completed ambient is proved).
\item Whether the coderived--chain transition across codim-1 loci
is controlled by a single universal residue formula; conjecturally
yes, via the Chenevier determinant of
\texttt{arithmetic\_shadows.tex}, currently open.
\end{itemize}

\textbf{What the attack did not break.} The unified form
$K^{2}\simeq\id$ on $\Kosz(X)$ survives with explicit chain-level
witnesses on all five classes. The coderived correction off
$\Kosz(X)$ is load-bearing but standard (Positselski). The
global form is a theorem via Francis--Gaitsgory + KZB
horizontality. The $(\infty,2)$-properad enhancement is
load-bearing and genuine. The universal chain homotopy is
archetype-rescaled Loday--Vallette.

\textbf{What the attack sharpened.} Priddy-for-$\mathsf{G}$,
Positselski-for-$\mathsf{L/C/M/B}$. The chain/coderived split is
not cosmetic. The archetype-specific rescaling of the homotopy by
$\kappa+\kappa^{!}$ is the link to Theorem~C. The global
$K^{\mathrm{univ}}$ assembly pinches at KZB horizontality, not at
the formal cobar--bar adjunction.

%--------------------------------------------------------------------
\subsection*{Concordance check}
%--------------------------------------------------------------------

Conventions used: $\Bbarch_X = \bar{B}^{\mathrm{ch}}_X$ (chiral
augmented bar); $\Omegach_X = \Omega^{\mathrm{ch}}_X$ (chiral cobar);
$\Kosz(X) \subset \Alg^{\fact,\aug,\comp}_X$ the Koszul locus;
$s^{-1}$ desuspension with $|s^{-1}v| = |v|-1$;
$B(A) = T^{c}(s^{-1}\bar A)$ as in
CLAUDE.md essential-constants. $\kappa+\kappa^{!}\in\{0,8,13,250/3,98/3\}$
from Theorem~C, classical classes from
\texttt{landscape\_census.tex}. Zamolodchikov norm
$\langle\Lambda|\Lambda\rangle = c(5c+22)/10$ with
$\Lambda = {:}TT{:} - (3/10)\partial^{2}T$ per CLAUDE.md.
Sugawara $T^{\mathrm{Sug}} = \tfrac{1}{2(k+h^{\vee})}\sum{:}J^{a}J^{a}{:}$
per \texttt{chiral\_koszul\_pairs.tex}. The
Loday--Vallette contracting homotopy is
\cite[eq.\ (2.17)]{LV12}; the chiral specialisation is
Corollary~\ref{cor:eight-cor-twisted-tensor} of
\texttt{theorem\_A\_infinity\_2.tex}. The Positselski coderived
equivalence $D^{\co}\simeq D^{\ctr}$ is
\cite[App.\ A.5]{Positselski2011}. The Francis--Gaitsgory
factorisation ambient is
\cite[\S4.2]{Francis2012} + \cite[Ch.\ IV.5]{GR17}. All consistent
with \texttt{chapters/connections/concordance.tex}.

No disagreement with concordance detected.

%--------------------------------------------------------------------
% End of agent_02_G1_koszul_reflection.tex
%--------------------------------------------------------------------
