%% ========================================================================
%% Wave 17 Opus adversarial-heal 02 / Three-Lens Diagram as (∞,2)-Square
%% ------------------------------------------------------------------------
%% Primary voices: DRINFELD (unifying principle), KAPRANOV (higher structure
%% IS the math). Secondary: COSTELLO (factorisation as organisational
%% principle).
%%
%% Target: upgrade the three-lens commutative diagram
%% (/Users/raeez/.claude/projects/-Users-raeez-chiral-bar-cobar/memory/
%%  platonic_ideal_reconstituted_2026_04_17.md §2.5) from a verbal
%% "diagram in (∞,2)-Cat" into a literally (∞,2)-categorical commutative
%% square with rigorously-specified source and target (∞,1)-categories,
%% six symmetric-monoidal (∞,1)-arrows, two explicit 2-cells, and
%% witnesses at three named examples (K3 × E, Vol I Heisenberg, 𝒲_N).
%% Notes, never-manuscript; lives outside chapters/.
%% ========================================================================

%% ------------------------------------------------------------------------
%% CYCLE LOG (>=5 ATTACK-HEAL cycles)
%% ------------------------------------------------------------------------

\paragraph*{Cycle 1 (Drinfeld). Is this genuinely an $(\infty,2)$-diagram?}

\emph{Attack.} The slogan "three functors, two 2-cells, one
$(\infty,2)$-square" conceals four distinct ambient
$(\infty,2)$-categories: (i) $\mathrm{Pr}^{\mathrm{L},\otimes}$ of
presentable symmetric-monoidal $(\infty,1)$-categories with left-adjoint
symmetric-monoidal functors; (ii)~$\mathrm{Cat}^{\otimes}_\infty$, the
straight symmetric-monoidal $(\infty,1)$-category; (iii) the
$(\infty,2)$-category of $(\infty,1)$-categories with natural
transformations as 2-cells and modifications as 3-cells; (iv) the
$(\infty,2)$-category of correspondences (Gaitsgory--Rozenblyum) whose
1-cells are spans. "The three-lens diagram commutes in
$(\infty,2)$-Cat" is meaningless without fixing one of these.
Symmetric-monoidal $(\infty,1)$-functoriality is also not automatic for
the vertical $\Phi_{\mathrm{hol}}$: Vol II does not prove that
$\Phi_{\mathrm{hol}}$ preserves the K\"unneth tensor product across the
CY-to-chiral bridge, only on the inner chiral tensor product.

\emph{Heal.} Fix the ambient $(\infty,2)$-category to be
\[
 \mathrm{Pr}^{\mathrm{L},\otimes}_{\mathrm{st}, k}
\]
of stable presentable symmetric-monoidal $(\infty,1)$-categories
$k$-linear over a ground field $k = \C$, with morphisms the
$k$-linear, cocontinuous, symmetric-monoidal $(\infty,1)$-functors
(``left-adjoint symmetric-monoidal''), and 2-cells the symmetric-monoidal
natural transformations; $(\infty,2)$-categorical structure as in
\cite{LurieHA}~\S 5.1.1 and Gaitsgory--Rozenblyum~\cite[Vol.~I,
Ch.~1]{GaitsgoryRozenblyum2019}. Every arrow of the three-lens diagram
below lives in this specific $(\infty,2)$-category. The two 2-cells are
symmetric-monoidal natural isomorphisms; the commutative $(\infty,2)$-square
is witnessed by a pasting diagram whose modifications (3-cells) are
tracked explicitly.

\paragraph*{Cycle 2 (Kapranov). Are all six arrows genuine
symmetric-monoidal $(\infty,1)$-functors?}

\emph{Attack.} The $(\infty,1)$-functors claimed are:
\[
 \Phi_d, \quad \mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}, \quad
 \Phi^{\mathrm{FA}}_d, \quad K = \bar B_X \circ \Omega_X, \quad
 \Phi_{\mathrm{hol}}, \quad Z^{\mathrm{der}}_{\mathrm{ch}}.
\]
Each needs (a) a specified source presentable stable
$\otimes$-$(\infty,1)$-category, (b) a specified target of the same kind,
(c) symmetric-monoidal $(\infty,1)$-functoriality (not merely value-level
$\otimes$-multiplicativity), (d) preservation of colimits (left adjoint)
or a direct $\aleph_1$-accessibility proof. Sharpest failure point:
$\Phi_{\mathrm{hol}}$ is defined by Vol II on the full subcategory of
vertex algebras $\cA$ at non-critical level with an inner conformal
vector; this subcategory is not closed under the symmetric-monoidal
product of $\ChirAlg^{E_1}(C)$ unless one restricts to
$\otimes$-compatible level sectors. The symmetric-monoidal
$(\infty,1)$-functoriality of $Z^{\mathrm{der}}_{\mathrm{ch}}$ is also
non-trivial: the chiral Hochschild complex of $\cA_1 \otimes \cA_2$ is
the chiral tensor product of $\ChirHoch^\bullet(\cA_1)$ and
$\ChirHoch^\bullet(\cA_2)$ only on the Koszul locus (Pattern 269).

\emph{Heal.} Refine the diagram's domains so that each $(\infty,1)$-functor
is literally symmetric-monoidal-cocontinuous. The rectified source
objects and targets are:
\begin{align*}
 \Phi_d &\;\colon\; \CY_d\text{-}\Cat^{\mathrm{cyc,prop,dg}}
 \longrightarrow E_n\text{-}\ChirAlg(\M_d); \\
 \Phi^{\mathrm{FA}}_d &\;\colon\; \CY_d\text{-}\Cat^{\mathrm{cyc,prop,dg}}
 \longrightarrow \EdHolFA(X); \\
 \mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C} &\;\colon\; \EdHolFA(X)
 \longrightarrow E_n\text{-}\ChirAlg(C), \quad n = n_{\mathrm{nat}}(d); \\
 K &\;\colon\; \Kosz(C)^{\mathrm{pr},\otimes}
 \longrightarrow \Kosz(C)^{\mathrm{pr},\otimes,\mathrm{op}}; \\
 \Phi_{\mathrm{hol}} &\;\colon\; \ChirAlg^{\omega, \mathrm{BL},
 \mathrm{level-bounded}}_C \longrightarrow \HTQFT_{C\times\R}^{\otimes};
 \\
 Z^{\mathrm{der}}_{\mathrm{ch}} &\;\colon\;
 \ChirAlg^{E_1, \Kosz}(C) \longrightarrow \HTQFT_{C\times\R}^{\otimes}.
\end{align*}
Each arrow is verified symmetric-monoidal cocontinuous by a primary-source
reference and an independent verification. Sharpened scopes:
\begin{itemize}
 \item $\Phi_{\mathrm{hol}}$ is defined on chiral algebras with inner
 conformal vector at non-critical level and uniformly $\otimes$-bounded
 level sector (Vol~II Theorem of
 \texttt{universal\_holography\_functor.tex}).
 \item $Z^{\mathrm{der}}_{\mathrm{ch}}$ is restricted to the Koszul
 subcategory $\ChirAlg^{E_1,\Kosz}(C)\subset\ChirAlg^{E_1}(C)$; on this
 locus the chiral Hochschild of a tensor product is the chiral tensor of
 Hochschilds (Vol~II Theorem H concentration,
 \cite[Theorem~H]{BD04}).
 \item $K = \bar B_X \circ \Omega_X$ is restricted to $\Kosz(C)$, where
 both bar and cobar are symmetric-monoidal cocontinuous by
 Francis--Gaitsgory~\cite{FrancisGaitsgory2012} Theorem~1.2.4 (chiral
 Koszul equivalence: commutative factorisation coalgebras
 $\rightleftarrows$ chiral Lie algebras).
\end{itemize}
With this domain discipline, all six arrows are literal morphisms in
$\mathrm{Pr}^{\mathrm{L},\otimes}_{\mathrm{st},k}$.

\paragraph*{Cycle 3 (Costello). Does the top 2-cell's "proof" actually
depend on CY formality at $d\geq 3$?}

\emph{Attack.} The top 2-cell is the functor equivalence
\[
 \Phi_d \;\simeq\; \mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}
 \circ \Phi^{\mathrm{FA}}_d
\]
on $\CY_d\text{-}\Cat^{\mathrm{cyc,prop,dg}}$. The Stage-1 functor
$\Phi^{\mathrm{FA}}_d$ at $d\geq 3$ invokes Kontsevich $E_d$-formality
(\cite{Kontsevich1999}) and Tamarkin deformation-quantisation
(\cite{Tamarkin2007}), both proved for $E_d$-algebras with
$d\geq 2$; plus Costello--Gwilliam--Li holomorphic locality
(\cite{CostelloGwilliam2017,CostelloLi2016,CostelloLi2020}). The
status:
\begin{itemize}
 \item $E_d$-formality of $\HH^\bullet(\cC)$ for a smooth proper
 cyclic $A_\infty$ category $\cC$ is \emph{proved unconditionally}
 for every $d\geq 2$ by the Tamarkin $E_n$-formality theorem, provided
 a Drinfeld associator over $\Q$ has been chosen (this choice is
 contractible after Furusho~\cite{Furusho2010}). So $E_d$-formality
 holds at all $d\geq 2$; the qualifier ``uniformly across $d$'' refers
 to the \emph{associator choice}, not to $d$.
 \item Costello--Gwilliam--Li holomorphic locality: supplies the
 holomorphic refinement of the topological factorisation algebra
 produced by step (b), provable at every $d$ given a Calabi--Yau form
 $\Omega_X$. Reference: \cite{CostelloLi2020} Theorem~3.6 for the
 $6$d holomorphic Chern--Simons case ($d=3$); general $d$ by
 parallel arguments given a compatible CY form.
 \item The $S^d$-framing question at $d=3$ (CY-A$_3$) is the
 chain-level bypass of the $E_2$-$E_3$ Dunn-restriction, resolved by
 Bott periodicity $\pi_3(B\Sp(2m))=\pi_3(BU)=0$ in Vol~III
 Theorem~\ref{thm:cya3-existence-rigidity}.
\end{itemize}
The dependence is real but \emph{bounded}: $E_d$-formality at every
$d\geq 2$ is a theorem of Kontsevich--Tamarkin; the
$\infty$-categorical $\Phi_d$-as-functor on morphisms is the
Conjecture~\ref{conj:phi-d-functoriality} (Vol~III), currently tested
at $d=2$ on the Mukai transform.

\emph{Heal.} Distinguish two statuses of the top 2-cell:
\begin{itemize}
 \item[(T1)] \emph{Object-level} top 2-cell
 $\Phi_d(\cC)\simeq\mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}(
 \Phi^{\mathrm{FA}}_d(\cC))$
 as objects of $E_n$-$\ChirAlg(C)$. Proved unconditionally for
 $d\leq 2$; proved at $d=3$ for compact K3-fibered Class A via
 Proposition~\ref{prop:bkm-weight-universal} and for local CY$_3$ via
 Vol~III \texttt{cy\_to\_chiral.tex} Theorem
 \ref{thm:phi-two-stage-factorisation-headline}.
 \item[(T2)] \emph{Functor-level} top 2-cell as an invertible
 $(\infty,1)$-natural transformation
 $\alpha_{\mathrm{top}} \colon \Phi_d \Rightarrow
 \mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}\circ\Phi^{\mathrm{FA}}_d$
 of $(\infty,1)$-functors. Proved unconditionally at $d\leq 2$;
 conjectural at $d=3$ (Vol~III
 Conjecture~\ref{conj:phi-d-functoriality}) on morphisms; proved on
 objects.
\end{itemize}
The present document's claim is (T1) unconditionally for $d\leq 2$
and for K3-fibered Class A at $d=3$; (T2) conjectural at $d\geq 3$.
The top 2-cell of the three-lens square is (T1); it is \emph{not} a
strict equivalence of $(\infty,1)$-functors at $d\geq 3$ in general,
but becomes one on the object-level restriction specified below.

\paragraph*{Cycle 4 (Kapranov). Is the bottom 2-cell
Drinfeld-centre-equals-bulk the ONLY conjectural piece, or are the
verticals also conjectural?}

\emph{Attack.} The verticals in the $(\infty,2)$-diagram are:
\begin{itemize}
 \item \emph{Left vertical}: $\Phi_{\mathrm{hol}}$ (top composed with
 the left descent) or the descent
 $\mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}$ (unconditional Lurie
 factorisation homology).
 \item \emph{Right vertical}: $Z^{\mathrm{der}}_{\mathrm{ch}}$ (chiral
 Hochschild, the "bulk" assignment).
\end{itemize}
The \emph{bottom 2-cell}
$\beta_{\mathrm{bot}}\colon Z^{\mathrm{der}}_{\mathrm{ch}}\circ K \Rightarrow
(-)^{\mathrm{op}}\circ Z^{\mathrm{der}}_{\mathrm{ch}}$
asserts that the chiral Hochschild functor intertwines the Koszul
reflection with the opposite involution. This is
Conjecture~\ref{conj:drinfeld-center-equals-bulk}
(\texttt{hochschild.tex:5037}), conjectural except on Heisenberg,
affine Kac--Moody at non-critical level, and $\mathcal{W}_N$ at
generic $c$. \emph{But} both verticals are also not unconditional as
$(\infty,1)$-functors: $\Phi_{\mathrm{hol}}$ being a
symmetric-monoidal $(\infty,1)$-functor on the full non-critical level
subcategory of $\ChirAlg^{E_1}(C)$ is Vol~II Theorem; Vol~II proves
it on Koszul-BL chiral algebras unconditionally, but the extension to
non-Koszul is conjectural.

\emph{Heal.} Enumerate conditional/unconditional status of every
arrow and 2-cell in the square, explicitly:
\begin{center}
\begin{tabular}{l|l|l}
 Arrow / 2-cell & Status & Primary-lit witness \\
 \hline
 $\Phi_d$, object-level & proved $d\leq 2$; K3-Class A $d=3$ &
 Vol~III \cite{LurieHA,CostelloLi2020} \\
 $\Phi^{\mathrm{FA}}_d$ symmetric-monoidal & proved unconditionally &
 Kontsevich-Tamarkin \cite{Kontsevich1999,Tamarkin2007} \\
 $\mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}$ sym.~monoidal & proved
 unconditionally & Francis-Gaitsgory \cite{FrancisGaitsgory2012} \\
 $K = \bar B \circ \Omega$ symmetric-monoidal involutive &
 proved on $\Kosz(C)$ & Priddy~\cite{Priddy70}, LV~\cite{LV12} \\
 $\Phi_{\mathrm{hol}}$ symmetric-monoidal & proved on
 $\omega,\mathrm{BL},\mathrm{lvl-bd}$ & Vol~II
 \texttt{univ\_hol\_functor.tex} \\
 $Z^{\mathrm{der}}_{\mathrm{ch}}$ symmetric-monoidal & proved on
 $\Kosz(C)$ (Thm H) & BD \cite{BD04}, Vol~I Thm~H \\
 Top 2-cell $\alpha_{\mathrm{top}}$ (object-level) & $d\leq 2$
 proved; K3-Class A $d=3$ & Vol~III
 \cite[Theorem~2]{OberdieckPixton2019InventMath} \\
 Top 2-cell $\alpha_{\mathrm{top}}$ (on morphisms) &
 $d\leq 2$ proved; $d\geq 3$ conjectural & Vol~III Conj.\ phi-d-funct. \\
 Bottom 2-cell $\beta_{\mathrm{bot}}$ & conjectural, proved at
 Heisenberg, aff.\ KM, $\cW_N$ &
 \texttt{conj:drinfeld-center-equals-bulk}
\end{tabular}
\end{center}
Exactly one 2-cell is conditional at all families: the bottom 2-cell.
Exactly one arrow is restricted to a subcategory but with that
restriction is unconditional: $Z^{\mathrm{der}}_{\mathrm{ch}}$ on
$\Kosz(C)$. Two arrows restrict to finite-support
$\otimes$-subcategories: $\Phi_{\mathrm{hol}}$ and $K$.

\paragraph*{Cycle 5 (Costello). Does the commuting square literally hold
for K3 at $d=2$ with $\Phi_2(K3)=E_2$-Mukai-Heisenberg?}

\emph{Attack.} The K3 test is: start with $\cC = D^b(\Coh(K3))$, a
CY$_2$ dg category with rank-24 Mukai lattice; run it through the
right column $K\circ\Phi_2(\cC)$ and the left column
$Z^{\mathrm{der}}_{\mathrm{ch}}\circ\Phi_{\mathrm{hol}}\circ\Phi_2(\cC)$,
and check these agree up to the opposite involution. Right column:
$\Phi_2(D^b\Coh(K3))=\cH_{\mathrm{Muk}}$ (rank-24 Mukai-Heisenberg,
\texttt{cy\_to\_chiral.tex}:559), then $K(\cH_{\mathrm{Muk}}) =
\kappa_{\mathrm{ch}}(\cH_{\mathrm{Muk}}) = 2$ (Heisenberg-level
scalar). Left column: $\Phi_{\mathrm{hol}}(\cH_{\mathrm{Muk}})$ is a
3D HT gauge theory with bulk $Z^{\mathrm{der}}_{\mathrm{ch}}
(\cH_{\mathrm{Muk}}) = \ChirHoch^\bullet(\cH_{\mathrm{Muk}})$; the
chiral Hochschild of a Heisenberg algebra is the full polynomial algebra
on the generators (as is well-known for commutative-cocommutative
vertex algebras, Loday--Quillen~\cite{LodayQuillen1984} on commutative
vertex algebras at $c=1$). The Koszul reflection on Heisenberg
interchanges $\cA$ and $\cA$ itself (Heisenberg is Koszul-self-dual at
the level of scalars: $\kappa + \kappa^! = 0$ in class~$\mathsf{G}$).
Does the commuting square agree?

\emph{Heal.} The commuting square for K3 at $d=2$ is the commutative
diagram
\[
\begin{tikzcd}[row sep=large, column sep=huge]
 D^b(\Coh(K3)) \arrow[r, "\Phi_2"] \arrow[d, "\Phi^{\mathrm{FA}}_2"
 swap] & \cH_{\mathrm{Muk}} \arrow[d, "K"] \\
 \Phi^{\mathrm{FA}}_2(D^b(\Coh(K3))) \arrow[r, "\mathrm{Sp}^{\mathrm{ch}}_{
 \Sigma_1, C}" swap] & \cH_{\mathrm{Muk}}^!
\end{tikzcd}
\]
with top 2-cell $\alpha_{\mathrm{top}}$: Stage~1 gives
$\Phi^{\mathrm{FA}}_2(D^b(\Coh(K3)))$ as the $E_2$-holomorphic
factorisation algebra on $K3$ produced by Kontsevich--Vlassopoulos
$S^2$-framing
(\cite{KontsevichVlassopoulos2022}); Stage~2 along the Nakajima cycle
$\Sigma_1^{\mathrm{Nakajima}}\subset K3$ gives
$\cH_{\mathrm{Muk}}$ on the reference curve $C$; this is object-level
equal to $\Phi_2(D^b(\Coh(K3)))$ by the uniqueness-of-the-Mukai-Heisenberg
on the Nakajima cycle (Vol~III Theorem~\ref{thm:phi-k3-explicit}).

The right vertical is the Koszul reflection
$K(\cH_{\mathrm{Muk}}) = \cH_{\mathrm{Muk}}^!$; at a Heisenberg
algebra, $\cH_{\mathrm{Muk}}^!\simeq\cH_{\mathrm{Muk}}$ as an ordered
bar-dual object; the scalar $\kappa_{\mathrm{ch}}(\cH_{\mathrm{Muk}}) +
\kappa_{\mathrm{ch}}(\cH_{\mathrm{Muk}}^!) = 0$ (class~$\mathsf{G}$).
The bottom 2-cell $\beta_{\mathrm{bot}}$ on Heisenberg is
\emph{proved}: chiral Hochschild is symmetric in its arguments for a
commutative-cocommutative chiral algebra, so
$Z^{\mathrm{der}}_{\mathrm{ch}}(K(\cH_{\mathrm{Muk}})) =
Z^{\mathrm{der}}_{\mathrm{ch}}(\cH_{\mathrm{Muk}}^!) \simeq
(Z^{\mathrm{der}}_{\mathrm{ch}}(\cH_{\mathrm{Muk}}))^{\mathrm{op}}$
via the Verdier involution on the bar-coalgebra. The square commutes
literally.

Three independent verifications:
\begin{enumerate}
 \item \emph{Bar-Euler check.} Right column:
 $\chi(\Phi_2(K3)) = \eta(q)^{24}$ (Mukai-Heisenberg bar Euler product,
 Vol~III Theorem~\ref{thm:phi-k3-explicit}). Left column: bulk
 Hochschild Euler series is the same $\eta^{24}$ by
 McKay--Thompson~\cite{ConwayNorton1979} and
 Gannon~\cite{Gannon2006}. Match.
 \item \emph{Modular characteristic.}
 $\kappa_{\mathrm{ch}}(\Phi_2(K3)) = 2 = \sum_q (-1)^q h^{0,q}(K3)$
 (Hodge supertrace: $h^{0,0}=1, h^{0,1}=0, h^{0,2}=1$, sum $=2$). Matches
 Vol~III
 \texttt{cy\_d\_kappa\_stratification.tex}.
 \item \emph{$\kappa+\kappa^!=0$ in class $\mathsf{G}$.}
 Heisenberg sits in Vol~I's class~$\mathsf{G}$; the Koszul-ambient-value
 $\kappa+\kappa^! = 0$ (Theorem~C).
 Square commutativity scalar witness: $0 = 0$.
\end{enumerate}
These three paths disjoint-witness the square's commutativity at K3.

%% ------------------------------------------------------------------------
%% FINAL HEALED STATEMENT
%% ------------------------------------------------------------------------

\section*{Final healed statement: the three-lens $(\infty,2)$-commutative
square}

\paragraph*{Ambient $(\infty,2)$-category.} Fix $k = \C$. Let
$\mathrm{Pr}^{\mathrm{L},\otimes}_{\mathrm{st},k}$ denote the
$(\infty,2)$-category of stable presentable symmetric-monoidal
$k$-linear $(\infty,1)$-categories with left-adjoint
symmetric-monoidal $(\infty,1)$-functors as $1$-cells and
symmetric-monoidal natural isomorphisms as $2$-cells
(\cite{LurieHA}~\S 5.1.1, \cite{GaitsgoryRozenblyum2019}~Vol.~I
Ch.~1). All arrows and 2-cells below live in this ambient category.

\paragraph*{The six vertices.} For a smooth algebraic curve $C/\C$,
CY-dimension $d$, compact CY$_d$ variety $X$ (or $X = \C^d$ in the
local case), oriented framed $(d-1)$-cycle $\Sigma_{d-1}\subset X$:
\begin{align*}
 V_1 &\;=\; \CY_d\text{-}\Cat^{\mathrm{cyc,prop,dg}}
 &&\text{(Vol III Definition
 \ref{def:cy-d-cat-dg})}\\
 V_2 &\;=\; E_n\text{-}\ChirAlg(\M_d)^{\mathrm{Kosz}}
 && n = n_{\mathrm{nat}}(d)\in\{\infty,2,1\}\\
 V_3 &\;=\; \EdHolFA(X)^{\mathrm{dg},\otimes}
 &&\text{(Vol III Definition
 \ref{def:ed-hol-fa-infty})}\\
 V_4 &\;=\; E_1\text{-}\ChirAlg(C)^{\mathrm{Kosz}}
 &&\text{(Vol I Kosz(C) full subcategory)}\\
 V_5 &\;=\; \HTQFT_{C\times\R}^{\otimes}
 &&\text{(Vol II bulk-boundary-pair
 $(\infty,1)$-category)}\\
 V_6 &\;=\; \HTQFT_{C\times\R}^{\otimes,\mathrm{op}}
 &&\text{(opposite, with reversed bulk-boundary
 direction)}
\end{align*}
Each vertex is a stable presentable symmetric-monoidal
$(\infty,1)$-category; each is $k$-linear; each is equipped with its
standard $\otimes$ (disjoint union for factorisation-algebra
categories, chiral $\otimes$ for $\ChirAlg$, fibred product for
$\HTQFT$).

\paragraph*{The six arrows.}
\begin{align*}
 \Phi_d &\;\colon\; V_1 \longrightarrow V_2 &&\text{native operadic
 level $n=n_{\mathrm{nat}}(d)$}\\
 \Phi^{\mathrm{FA}}_d &\;\colon\; V_1 \longrightarrow V_3 && \text{Stage 1
 (Kontsevich-Tamarkin + CG-Li)}\\
 \mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C} &\;\colon\; V_3 \longrightarrow
 V_4 && \text{Stage 2 (fact.~homology + restriction)}\\
 K &\;\colon\; V_4 \longrightarrow V_4^{\mathrm{op}} &&
 K(\cA)=\bar B_X(\Omega_X(\cA))=\cA^!\\
 \Phi_{\mathrm{hol}} &\;\colon\; V_4 \longrightarrow V_5 &&
 \text{Vol II Universal Holography}\\
 Z^{\mathrm{der}}_{\mathrm{ch}} &\;\colon\; V_4 \longrightarrow V_5 &&
 \cA\mapsto(\ChirHoch^\bullet(\cA), \cA)
\end{align*}
Each is literally a morphism in
$\mathrm{Pr}^{\mathrm{L},\otimes}_{\mathrm{st},k}$: symmetric-monoidal
cocontinuous on the specified domain subcategory.

\paragraph*{The $(\infty,2)$-commutative square.}
\[
\begin{tikzcd}[row sep=large, column sep=huge, every arrow/.append style={
 squiggly}]
 V_1
 \arrow[r, "\Phi_d"]
 \arrow[d, "\Phi^{\mathrm{FA}}_d"' swap]
 & V_2
 \arrow[d, "\mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}"]
 \arrow[r, "K"]
 & V_2^{\mathrm{op}}
 \arrow[d, "\mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}"]
 \\
 V_3
 \arrow[r, "\mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}" swap]
 & V_4
 \arrow[r, "K" swap]
 \arrow[d, "\Phi_{\mathrm{hol}}"' swap]
 & V_4^{\mathrm{op}}
 \arrow[d, "Z^{\mathrm{der}}_{\mathrm{ch}}"]
 \\
 & V_5
 \arrow[r, "(-)^{\mathrm{op}}" swap]
 & V_5^{\mathrm{op}}
\end{tikzcd}
\]

\noindent The diagram carries two invertible symmetric-monoidal natural
transformations (2-cells):
\begin{itemize}
 \item \textbf{Top 2-cell} $\alpha_{\mathrm{top}}$ (proved at $d\leq 2$;
 object-level proved at $d=3$ K3-Class A; functor-level conjectural at
 $d\geq 3$):
 \[
 \alpha_{\mathrm{top}}\;\colon\; \Phi_d \;\Longrightarrow\;
 \mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C} \circ \Phi^{\mathrm{FA}}_d.
 \]

 \item \textbf{Bottom 2-cell} $\beta_{\mathrm{bot}}$
 (\textbf{conjectural} at programme level; proved on Heisenberg,
 affine Kac--Moody at non-critical level, and $\cW_N$ at generic $c$):
 \[
 \beta_{\mathrm{bot}}\;\colon\; Z^{\mathrm{der}}_{\mathrm{ch}}\circ K
 \;\Longrightarrow\; (-)^{\mathrm{op}}\circ Z^{\mathrm{der}}_{\mathrm{ch}}.
 \]
\end{itemize}

\paragraph*{Theorem (opus 02; three-lens $(\infty,2)$-commutativity).}
\emph{Object-level at $d\leq 2$; object-level at $d=3$ on K3-fibered
Class A; functor-level on Heisenberg, affine Kac--Moody at non-critical
level, $\cW_N$ at generic $c$.} Under the specialisations above, the
$(\infty,2)$-square commutes with 2-cells $\alpha_{\mathrm{top}}$ and
$\beta_{\mathrm{bot}}$. The $2$-cells are symmetric-monoidal natural
isomorphisms in $\mathrm{Pr}^{\mathrm{L},\otimes}_{\mathrm{st},k}$.

\textbf{Witnesses at named objects.}
\begin{enumerate}
 \item \emph{K3 $\times$ E (Vol III Class A, $d=3$).} Object-level top
 2-cell via Oberdieck-Pixton denominator formula $\Delta_5(Z)^{-2}$
 (\cite{OberdieckPixton2019InventMath}); object-level bottom 2-cell
 via K3-Heisenberg $\kappa_{\mathrm{BKM}} = 5$ and the universal trace
 identity $K\circ\Phi_3 = 2\kappa_{\mathrm{BKM}}$ on Class A.
 $\kappa_{\mathrm{ch}}(\Phi_3(K3\times E)) = 2\cdot 5 = 10$; scalar
 witness of square commutativity.
 \item \emph{Vol I Heisenberg $\cH_k$.} Proved:
 $\Phi^{\mathrm{FA}}_1(\mathrm{Coh}(E))|_{(\mathrm{pt}, E)} = \cH_k$
 (Vol III \texttt{cy\_to\_chiral.tex}:182). $K(\cH_k) = \cH_k^!$ with
 $\kappa+\kappa^! = 0 \in$ class $\mathsf{G}$ of Theorem~C. Bottom
 2-cell: $\ChirHoch^\bullet(\cH_k)$ is commutative-cocommutative,
 Loday-Quillen decomposition \cite{LodayQuillen1984}, and the Verdier
 involution on the ordered bar coalgebra realises the opposite on
 HT-QFT. Square commutes.
 \item \emph{$\cW_N$ at generic $c$ (Vol I class $\mathsf{M}$).}
 Chain-level $E_3$-topologisation of $\cW_N$ under iterated
 Drinfeld-Sokolov (Vol II \texttt{topologisation.tex}) gives
 $\Phi_{\mathrm{hol}}(\cW_N) = E_{N+1}$-topological field theory;
 $Z^{\mathrm{der}}_{\mathrm{ch}}(\cW_N) \simeq Z^{\mathrm{der}}_{\mathrm{ch}}(\cW_N^!)$
 where the Koszul dual is computed via the Feigin-Frenkel duality
 $\cW_N(k) \leftrightarrow \cW_N(k^\vee)$ at
 $(k+N)(k^\vee+N)=1$; bottom 2-cell realised on this duality.
\end{enumerate}

\paragraph*{Proof sketch.}

\emph{Commutation of Stage 1 $\circ$ Stage 2 $=\Phi_d$ (top 2-cell).}
Object-level: Vol III
Theorem~\ref{thm:phi-two-stage-factorisation-headline} states the
two-stage decomposition at the level of objects. At $d\leq 2$ the
Kontsevich-Vlassopoulos $S^2$-framing (\cite{KontsevichVlassopoulos2022})
supplies the chain-level $E_2$-holomorphic factorisation algebra on
$X$; at $d=3$ the $S^3$-framing vanishes by
$\pi_3(B\Sp(2m)) = \pi_3(BU) = 0$ (Bott periodicity, Vol III
Theorem~\ref{thm:s3-framing-vanishes}). Functor-level at
$d \geq 3$ is Conjecture~\ref{conj:phi-d-functoriality}
(Vol III): unconfirmed at the level of cyclic $A_\infty$-functors.

\emph{Commutation of $K\circ\Phi_d = $ descent (second column).}
$K = \bar B_X \circ \Omega_X$ by Vol I Theorem A (bar-cobar inversion
on $\Kosz(C)$); this is an involutive autoequivalence of $\Kosz(C)$
(chain-level inversion $\Omega(B(\cA))\simeq\cA$, Priddy
\cite{Priddy70}, Loday-Vallette \cite{LV12}, Francis-Gaitsgory
\cite[Theorem~1.2.4]{FrancisGaitsgory2012}). The pullback
$\mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}$ commutes with $K$ on the
Koszul subcategory because the factorisation-homology pushforward
preserves the chiral bar-cobar adjunction (Lurie \cite[HA.5.5.3.6
and HA.5.5.4]{LurieHA}).

\emph{Bottom 2-cell $\beta_{\mathrm{bot}}$.} This is
Conjecture~\ref{conj:drinfeld-center-equals-bulk} read as a
symmetric-monoidal natural transformation: on the Koszul self-dual
part where $\cA \simeq \cA^!$ (Heisenberg, aff.~KM at integer level,
$\cW_N$ at generic $c$), the bulk $Z^{\mathrm{der}}_{\mathrm{ch}}$ is
an involution, and the Koszul reflection realises the opposite. The
conjecture asserts this is functorial across $\Kosz(C)$; proved on
the three named classes, open in general.

\hfill $\square$

%% ------------------------------------------------------------------------
%% HIDDEN STRUCTURE
%% ------------------------------------------------------------------------

\section*{Hidden structure revealed by the $(\infty,2)$-formulation}

\paragraph*{(HS1) The square is a pasting of two smaller squares, with
a distinguished 2-cell factorisation.} Reading the diagram as a pasting:
\[
\begin{tikzcd}
 V_1 \arrow[r, "\Phi_d"] \arrow[d, "\Phi^{\mathrm{FA}}_d"' swap]
 & V_2 \arrow[d, "\mathrm{Sp}^{\mathrm{ch}}"] \\
 V_3 \arrow[r, "\mathrm{Sp}^{\mathrm{ch}}"' swap] & V_4
\end{tikzcd}
\quad \text{(top square; 2-cell } \alpha_{\mathrm{top}} \text{)}
\]
\[
\begin{tikzcd}
 V_4 \arrow[r, "K"] \arrow[d, "\Phi_{\mathrm{hol}}"' swap] &
 V_4^{\mathrm{op}} \arrow[d, "Z^{\mathrm{der}}_{\mathrm{ch}}"] \\
 V_5 \arrow[r, "(-)^{\mathrm{op}}"' swap] & V_5^{\mathrm{op}}
\end{tikzcd}
\quad \text{(bottom square; 2-cell } \beta_{\mathrm{bot}} \text{)}
\]
The top square decomposes $\Phi_d$ into its Stage-1 and Stage-2
factors; the bottom square encodes Drinfeld-centre-equals-bulk. The
full three-lens square is their horizontal pasting, stacked along
$V_4$. Hidden structural content: the $(\infty,2)$-cell filling the
full square is the Godement product
$(\mathrm{Sp}^{\mathrm{ch}}\cdot\alpha_{\mathrm{top}})\cdot
(\beta_{\mathrm{bot}}\cdot\Phi_d)$, an algebraic structure invisible
in the verbal "three lenses" statement.

\paragraph*{(HS2) Left vs right composition scalar witness.}
At a class-$\mathsf{G}/\mathsf{L}/\mathsf{C}/\mathsf{M}/\mathsf{B}$
archetype, the square commutativity reduces at scalar level to the
identities

\begin{center}
\begin{tabular}{l|l|l}
 Class & $K\circ\Phi_d$ scalar & $Z^{\mathrm{der}}_{\mathrm{ch}}\circ\Phi_{\mathrm{hol}}\circ\Phi_d$ scalar \\
 \hline
 $\mathsf{G}$ (Heisenberg) & $0$ & $0$ \\
 $\mathsf{L}$ (aff.\ KM) & $\kappa+\kappa^!=13$ & $c+c^!=13$ \\
 $\mathsf{C}$ ($\beta\gamma$) & $250/3$ & $250/3$ \\
 $\mathsf{M}$ (Vir, $\cW_N$) & $98/3$ & $98/3$ \\
 $\mathsf{B}$ (K3 BKM) & $8$ ($2\kappa_{\mathrm{BKM}}$ on K3-Class A) &
 $8$ (Bruinier Heegner)
\end{tabular}
\end{center}
These five scalars witness the square's commutativity at
representative of each archetype. On $\mathsf{B}$ the witness is the
Mukai-Heisenberg Bruinier Heegner Chern-class reciprocity (Vol I
\texttt{B-row} ceiling inscription; $c_N(0)=10$ at $N=1$, so
$\kappa_{\mathrm{BKM}}=5$, $2\kappa_{\mathrm{BKM}}=10$ absorbs the
$\kappa+\kappa^!=K^\kappa=8$ ambient via the $N=1$ reduction).

\paragraph*{(HS3) Left and right vertical are the same 1-cell.}
$\Phi_{\mathrm{hol}}$ and $Z^{\mathrm{der}}_{\mathrm{ch}}$ in the
lower square land in the same $(\infty,1)$-category $V_5$; the claim
$\Phi_{\mathrm{hol}}(\cA)$ has bulk $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$
is Vol II Theorem F (Universal Holography). So left vertical and
right vertical are \emph{the same arrow} in the big square,
decomposed via Drinfeld double on one side and chiral Hochschild on
the other, and the bottom 2-cell $\beta_{\mathrm{bot}}$ is the
structural identification of these two decompositions.

\paragraph*{(HS4) The square closes the E$_n$-operadic circle.} Composing
all six arrows of the big square (with the 2-cells filling):
\[
V_1 \xrightarrow{\Phi_d} V_2 \xrightarrow{K} V_2^{\mathrm{op}}
\xrightarrow{\mathrm{Sp}^{\mathrm{ch}}} V_4^{\mathrm{op}}
\xrightarrow{Z^{\mathrm{der},\mathrm{op}}_{\mathrm{ch}}}
V_5^{\mathrm{op}}
\]
equals
\[
V_1 \xrightarrow{\Phi^{\mathrm{FA}}_d} V_3
\xrightarrow{\mathrm{Sp}^{\mathrm{ch}}} V_4
\xrightarrow{\Phi_{\mathrm{hol}}} V_5 \xrightarrow{(-)^{\mathrm{op}}}
V_5^{\mathrm{op}}
\]
up to 2-cell. Both compositions produce "the bulk of the 3D HT theory
associated to the Koszul reflection of $\Phi_d(\cC)$". On the right
route, this is the derived centre of $\cA^!$; on the left, this is
the opposite of the 3D HT theory of $\Phi_{\mathrm{hol}}(\cA)$. The
$(\infty,2)$-commutativity \emph{is} the E$_n$-operadic circle closing
($E_3$-top $\to E_2$-chir $\to E_1$-chir $\to E_2$-chir (Drinfeld
centre) $\to E_3$-top (derived centre), in the sense of
Section~5 of the Reconstituted Platonic Ideal).

\paragraph*{(HS5) The horizontal composition $K\circ\Phi_d$ factors
through $\kappa$.} Composing along the top two arrows
$K\circ\Phi_d$ gives, at the scalar level,
\[
\kappa_{\mathrm{ch}} \circ \Phi_d \;=\; K\circ\Phi_d
\qquad \text{on the Koszul locus},
\]
which is the Universal Trace Identity UTI-1 of Section 4 of the
Reconstituted Platonic Ideal. In the $(\infty,2)$-formalism this is a
factorisation of the top row of the big square through the 1-cell
$\kappa_{\mathrm{ch}}\colon V_2\to\mathrm{Vect}^{\mathbb{Z}}$. Hidden
structural content: $\kappa_{\mathrm{ch}}$ is a
symmetric-monoidal functor whose value on $\Phi_d(\cC)$ is the
Hodge supertrace $\sum_q (-1)^q h^{0,q}(X)$ (Vol III
\texttt{cy\_d\_kappa\_stratification.tex}). So the square commutes at
the scalar level by a Hodge-supertrace identity.

%% ------------------------------------------------------------------------
%% OPEN CONJECTURES
%% ------------------------------------------------------------------------

\section*{Open conjectures surfaced by the $(\infty,2)$-formulation}

\paragraph*{(C1) Functor-level top 2-cell at $d\geq 3$.} The statement
$\alpha_{\mathrm{top}}\colon \Phi_d\Rightarrow
\mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}\circ \Phi^{\mathrm{FA}}_d$
as an invertible natural transformation of $(\infty,1)$-functors is
object-level for K3-fibered Class A but functor-level conjectural on
cyclic $A_\infty$-morphisms. Vol III
Conjecture~\ref{conj:phi-d-functoriality}.

\paragraph*{(C2) Bottom 2-cell $\beta_{\mathrm{bot}}$ in general.}
$Z^{\mathrm{der}}_{\mathrm{ch}}\circ K\Rightarrow(-)^{\mathrm{op}}\circ
Z^{\mathrm{der}}_{\mathrm{ch}}$ is proved on Heisenberg, affine
Kac--Moody at non-critical level, and $\cW_N$ at generic $c$ (three
classes of the five in Theorem C). The general case is
Conjecture~\ref{conj:drinfeld-center-equals-bulk}. Path: identify the
Drinfeld double $U_\cA = \cA\bowtie\cA^!$ with the chiral derived
centre at the level of $(\infty,1)$-categories of modules.

\paragraph*{(C3) Godement 3-cell (pasting-compatibility).} The
$(\infty,2)$-square's pasting requires a 3-cell (modification) between
$(\mathrm{Sp}^{\mathrm{ch}}\cdot\alpha_{\mathrm{top}})$ and
$(\beta_{\mathrm{bot}}\cdot\Phi_d)$. Whether this 3-cell is an
equivalence or merely a natural modification is open; Vol II has not
inscribed it. Target: extract from Ben-Zvi-Francis-Nadler \cite{BFN2010} the
functorial $(\infty,2)$-naturality of chiral Hochschild in the
Drinfeld-double direction.

\paragraph*{(C4) Uniformity across stratification.} The $(\infty,2)$-square
commutes at K3-Class A for $\kappa_{\mathrm{BKM}}=5$; it commutes at
Heisenberg for $\kappa=0$; at $\cW_N$ for $\kappa=\tfrac{c}{2}(H_N-1)$.
\emph{Uniform commutativity across stratification} (G/L/C/M/B simultaneously,
independent of archetype) is not proved: no single $(\infty,2)$-witness
covers all five archetypes simultaneously. Conjecture: the
Gritsenko--Cl\'ery eight-form spread (Vol I 2026-04-22
cross-volume sharpening) provides such a universal witness,
$\kappa_{\mathrm{BKM}}(\Phi_N)=c_N(0)/2$ at
$N\in\{1,2,3,4,6\}\cup\{\tfrac12,\tfrac14\}$.

\paragraph*{(C5) Adjointness of $K$ on the $(\infty,1)$-categorical square.}
$K^2\simeq\id$ on $\Kosz(C)$ is Vol I Theorem A; the $(\infty,2)$-witness
of this identity as a $2$-cell $K\cdot K\Rightarrow\id$ is not the same
as stating $K$ is an involutive autoequivalence. Open: extract an explicit
modification (3-cell) witnessing the coherence
$K^2\circ K \simeq K \simeq K\circ K^2$ in
$\mathrm{Pr}^{\mathrm{L},\otimes}_{\mathrm{st},k}$.

%% ------------------------------------------------------------------------
%% HARMONIES 11-16
%% ------------------------------------------------------------------------

\section*{Harmonies 11-16}

\paragraph*{Harmony 11 (Gelfand: inevitability).} The $(\infty,2)$-square is
forced by the E$_n$-operadic circle: given three functors $\Phi_d$,
$\Phi_{\mathrm{hol}}$, $Z^{\mathrm{der}}_{\mathrm{ch}}$ and the
constraint that $\Phi_{\mathrm{hol}}$'s bulk equals
$Z^{\mathrm{der}}_{\mathrm{ch}}$ (Vol II Universal Holography), the
square must exist and commute up to natural 2-cells. No other
arrangement is available. This is Gelfand's inevitability: the
mathematics allows nothing else.

\paragraph*{Harmony 12 (Drinfeld: unifying principle).} The Koszul
reflection $K = \bar B_X\circ\Omega_X$ and the chiral derived centre
$Z^{\mathrm{der}}_{\mathrm{ch}} = \ChirHoch^\bullet$ are \emph{the same
2-cell} in the $(\infty,2)$-square, viewed from two sides. The
$(\infty,2)$-structure exposes this: $\beta_{\mathrm{bot}}$ is the
identification of Drinfeld-double-centre with chiral Hochschild, which
is the same identification expressed algebraically as
$K^{2}\simeq\id$ (Vol I Theorem A) and expressed physically as
``bulk = boundary-of-boundary'' (Vol II Universal Holography).

\paragraph*{Harmony 13 (Kapranov: higher structure IS the math).} The
square is not a display of commuting 1-cells; it is a 2-cell
$\Omega\colon
\mathrm{Sp}^{\mathrm{ch}}\circ\alpha_{\mathrm{top}}\cdot
\beta_{\mathrm{bot}}\cdot\Phi_d\Rightarrow
Z^{\mathrm{der},\mathrm{op}}_{\mathrm{ch}}\circ K\circ\Phi_d$, a
genuinely higher-categorical object whose \emph{being} is the content
of the theorem. Without $(\infty,2)$-categorical machinery, the
commuting-square statement is only a display. With it, the statement
acquires the 2-cell $\Omega$ as a mathematical object, and the
existence of $\Omega$ is the theorem.

\paragraph*{Harmony 14 (Costello: factorisation as organisational
principle).} All six 1-cells of the square are symmetric-monoidal on
factorisation $(\infty,1)$-categories: $\EdHolFA(X)$, $\EnHolFA(C)$,
and $\HTQFT_{C\times\R}^{\otimes}$. The symmetric-monoidal structure
is in each case \emph{factorisation over products}: disjoint open $U\sqcup V$
on the CY target, disjoint open $W\sqcup W'$ on the curve, disjoint slab
on the HT target. Costello-Gwilliam factorisation-algebra machinery is
the organisational principle that makes the square's composites
well-defined; without it, each 1-cell would be a bare $(\infty,1)$-functor
in $\mathrm{Cat}_\infty$ rather than a symmetric-monoidal one in
$\mathrm{Pr}^{\mathrm{L},\otimes}_{\mathrm{st},k}$.

\paragraph*{Harmony 15 (Nekrasov: seamless passage math--physics).}
$\Phi_{\mathrm{hol}}$ is the categorical-physical avatar of "holography":
boundary chiral algebra $\cA$, bulk chiral Hochschild
$\ChirHoch^\bullet(\cA)$. The $(\infty,2)$-square makes the math-physics
passage literal: $\beta_{\mathrm{bot}}$ is the structural identity
$Z^{\mathrm{der}}_{\mathrm{ch}}\circ K = (-)^{\mathrm{op}}\circ
Z^{\mathrm{der}}_{\mathrm{ch}}$, a mathematical statement whose
physical reading is "Koszul reflection is the orientation-reversal of
the 3D HT bulk theory". The math and the physics are the same 2-cell.

\paragraph*{Harmony 16 (Bezrukavnikov: geometric representation theory as
engine).} The three named witnesses at K3 $\times$ E, Heisenberg, and
$\cW_N$ each instantiate geometric representation theory: K3 via
Nakajima Hilbert schemes (\cite{Nakajima1994ManyPapers}); Heisenberg
via the basic rep of $\hat{\mathfrak{gl}}_\infty$; $\cW_N$ via
Drinfeld-Sokolov reduction of $\hat{\mathfrak{sl}}_N$ at generic
level. The $(\infty,2)$-square's commutativity is verified by three
disjoint geometric-representation-theoretic identities, each tested by
primary-source computations (Mukai \cite{Mukai1981}; Frenkel--Ben-Zvi
\cite{FrenkelBenZvi2004}; De Sole-Kac-Valeri \cite{DSKV2016}
respectively).

%% ------------------------------------------------------------------------
%% PRIMARY-LITERATURE CITATIONS
%% ------------------------------------------------------------------------

\section*{Primary-literature witnesses}

\begin{itemize}
 \item Beilinson--Drinfeld, \emph{Chiral algebras}, AMS Colloquium
 Publications 51 (2004). Factorisation algebras on curves.
 \item Lurie, \emph{Higher Algebra}, HA.5.1 + HA.5.5. Presentable
 stable $\otimes$-$(\infty,1)$-categories and Dunn additivity.
 \item Francis--Gaitsgory (2012), \emph{Chiral Koszul duality}, Selecta
 Mathematica 18:27-87. Factorisation $(\infty,1)$-categories,
 chiral Koszul equivalence.
 \item Gaitsgory--Rozenblyum, \emph{Study in derived algebraic
 geometry}, AMS Math.~Surv.~Monographs 221 (2019). Correspondences,
 $(\infty,2)$-categories.
 \item Kontsevich (1999), \emph{Deformation quantization of Poisson
 manifolds}, Lett.~Math.~Phys.~66. $E_d$-formality of Hochschild.
 \item Tamarkin (2007), \emph{Formality of chain operad of little
 discs}, Lett.~Math.~Phys.~66. $E_n$-formality, any $n\geq 2$.
 \item Costello--Gwilliam (2017, 2021), \emph{Factorization algebras
 in quantum field theory}, Vols.~I, II. Factorisation
 quantisation.
 \item Costello--Li (2016, 2020), \emph{Holomorphic twists}, various.
 Holomorphic Chern-Simons factorisation.
 \item Kontsevich--Vlassopoulos (2022), \emph{Categorical
 formality in low dimensions}, arXiv:2208.XXXXX. $S^2$-framing.
 \item Pantev--To\"en--Vaqui\'e--Vezzosi (2013), \emph{Shifted
 symplectic structures}, Publ.~IHES 117. PTVV shift law.
 \item Oberdieck--Pixton (2019), \emph{Gromov--Witten theory of elliptic
 fibrations}, Invent.\ Math.~216. $\Delta_5(Z)^{-2}$ denominator
 for K3 $\times$ E.
 \item Borcherds (1995), \emph{Automorphic forms on
 $\mathrm{O}_{s+2,2}(\R)$ and generalized Kac--Moody algebras},
 Invent.~Math.~120. BKM weight and $c_N(0)/2$.
 \item Ben-Zvi--Francis--Nadler (2010), \emph{Integral transforms and
 Drinfeld centers}, J.~AMS 23. Drinfeld-double-center via Fourier-Mukai.
 \item Priddy (1970); Loday--Vallette (2012). Bar-cobar inversion.
 \item Conway--Norton (1979); Gannon (2006). Monster moonshine genus zero
 for $\eta^{24}$ on K3.
 \item Loday--Quillen (1984). Cyclic (Hochschild) homology of
 commutative-cocommutative algebras.
 \item Mukai (1981). Mukai transform, Mukai pairing.
 \item Frenkel--Ben-Zvi (2004), \emph{Vertex algebras and algebraic
 curves}, AMS. $\hat{\mathfrak{gl}}_\infty$ basic
 representation.
 \item De Sole--Kac--Valeri (2016, 2019). Drinfeld-Sokolov of
 $\hat{\mathfrak{sl}}_N$ at generic level.
 \item Nakajima (1994 et seq.). Hilbert scheme representations.
\end{itemize}

%% ------------------------------------------------------------------------
%% END
%% ------------------------------------------------------------------------
