\documentclass[11pt]{article}

%%% Packages
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage[shortlabels]{enumitem}
\usepackage{booktabs}
\usepackage{array}
\usepackage{microtype}
\usepackage[colorlinks=true,linkcolor=blue!60!black,
 citecolor=green!40!black,urlcolor=blue!60!black]{hyperref}

%%% Page geometry
\usepackage[margin=1.15in]{geometry}

%%% Theorem environments
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{construction}[theorem]{Construction}
\newtheorem{example}[theorem]{Example}
\newtheorem{computation}[theorem]{Computation}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{warning}[theorem]{Warning}

%%% Macros
\newcommand{\fg}{\mathfrak{g}}
\newcommand{\fh}{\mathfrak{h}}
\newcommand{\fn}{\mathfrak{n}}
\newcommand{\fsl}{\mathfrak{sl}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cW}{\mathcal{W}}
\newcommand{\Defcyc}{\mathrm{Def}_{\mathrm{cyc}}}
\newcommand{\MC}{\mathrm{MC}}
\newcommand{\Sh}{\mathrm{Sh}}
\newcommand{\Res}{\operatorname{Res}}
\newcommand{\DS}{\mathrm{DS}}
\newcommand{\Vir}{\mathrm{Vir}}
\DeclareMathOperator{\rk}{rk}
\DeclareMathOperator{\ad}{ad}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\depth}{depth}
\numberwithin{equation}{section}

%%% Title
\title{Bershadsky--Polyakov Koszul self-duality\\
and the hook-type transport}
\author{Raeez Lorgat}
\date{}

\begin{document}
\maketitle

% ================================================================
% ABSTRACT
% ================================================================

\begin{abstract}
The Bershadsky--Polyakov algebra $\cB^k = W_k(\fsl_3, f_{(2,1)})$
is the Drinfeld--Sokolov reduction of $\widehat{\fsl}_3$ at the
minimal nilpotent orbit. We prove that, for $k \neq -3$ (away from the critical level), it is Koszul self-dual under
the hook-transpose involution: the partition $(2,1)$ is self-transpose
in the sense of Young diagrams, and the Koszul dual
$(\cB^k)^! \cong \cB^{k'}$ with $k' = -k-6$ is again a
Bershadsky--Polyakov algebra. The central sharpening of this note
(Theorem~\textup{\ref{thm:bp-koszul-conductor-polynomial}}) is the
\emph{polynomial identity} $K_{\cB}(k) \equiv 196$ in the rational
function field $\bQ(k)$, in the Arakawa/Fehily--Kawasetsu--Ridout
convention; equivalently, $c(\cB^k) - 98$ is an odd function of
$(k+3)$. The fixed point $k=-3$ of the level involution $k\mapsto -k-6$
coincides with the critical level $-h^\vee(\fsl_3)$, and
$\kappa(\cB^{-3}) = 49/3$ is the principal-value symmetric limit across
the pole, not a function value. Throughout this note
$\kappa_{\cB} = \tfrac{1}{6}\, c_{\cB}$ is the Bershadsky--Polyakov
modular-characteristic normalisation
(Chapter~\ref{chap:subregular-hook-frontier}), so that
$49/3 = (98)/6$ recovers the symmetric limit of $c$. In the Fateev--Lukyanov screening
convention used by the Vol~II counterparts, a direct rational
computation gives $K^{\mathrm{FL}}_{\cB}(k) = [(2k+9)(3k+17) - (2k+3)(3k+1)]/(k+3) = 50(k+3)/(k+3) \equiv 50$ in $\mathbb{Q}(k)$ (the pole at
$k=-3$ is removable); both conventions therefore produce a
level-independent polynomial-constant conductor, and they differ
only in numerical value (Arakawa $\equiv 196$ vs.\ Fateev--Lukyanov
$\equiv 50$) through the choice of central-charge normalisation.
The complementarity sum $\kappa_T + \kappa_T' = K_{\cB}/2 = 98 \neq 0$
is the first non-principal instance of a non-vanishing complementarity
in the $W$-algebra landscape. The shadow obstruction tower is class~$M$
on the $T$-line and class~$G$ on the $J$-line. All claims are verified
by $73+7$ tests with two independent HZ-IV decorators in the compute
layer.
\end{abstract}

\begin{remark}[Wave-14 reconstitution anchor]\label{rem:wave14-anchor-bp}
This standalone is the companion inscription of the Platonic theorem
\textup{\ref{thm:bp-koszul-conductor-polynomial}} at
Vol~I~\verb|standalone/bp_self_duality.tex:253| (this file) and its
Vol~II cross-check at
\verb|bp_chain_level_strict_platonic.tex| (FL convention). The
polynomial-identity theorem supersedes the earlier scalar
``$K_{\cB}=196$'' inscription by exhibiting the statement as an identity
of rational functions. The Arakawa-convention fixed-point $k=-3$
coincides with the critical level $-h^\vee(\fsl_3)$; the passage
through the removable singularity is not a value but a principal-value
symmetric limit. Both conventions (Arakawa and Fateev--Lukyanov)
produce a level-independent polynomial-constant Koszul conductor
(Arakawa $\equiv 196$, Fateev--Lukyanov $\equiv 50$; see
Remark~\ref{rem:bp-fl-convention-2026-04-17}); the two numerical
values are central-charge normalisations of the same algebra.
\end{remark}

% ================================================================
\section{Introduction}\label{sec:intro}
% ================================================================

The hook-type transport programme, initiated by Fehily
\cite{FehilyHook} and developed by Creutzig--Linshaw--Nakatsuka--Sato
\cite{CLNS24}, identifies a corridor in the non-principal $W$-algebra
landscape where Drinfeld--Sokolov reduction commutes with bar-cobar
duality. The corridor consists of $W$-algebras
$W_k(\fsl_N, f_\lambda)$ for hook-type partitions
$\lambda = (N-j, 1^j)$. For these partitions the transpose
$\lambda^t$ is again a hook: $(N-j, 1^j)^t = (j+1, 1^{N-j-1})$, and
the transport-to-transpose conjecture asserts
\begin{equation}\label{eq:transport-conjecture}
 \bigl(W_k(\fsl_N, f_\lambda)\bigr)^!
 \;\cong\;
 W_{k^\vee_\lambda}(\fsl_N, f_{\lambda^t})
\end{equation}
for a specific dual level $k^\vee_\lambda$ determined by the
Feigin--Frenkel involution of the Levi subalgebra.

The simplest non-trivial case is $N=3$, $\lambda = (2,1)$. Here
$\lambda^t = (2,1) = \lambda$: the partition is self-transpose. The
corresponding $W$-algebra is the Bershadsky--Polyakov algebra
$\cB^k$, the DS reduction of $\widehat{\fsl}_3$ at the minimal
nilpotent. At generic level ($k \neq -3$), self-transposition of the partition forces Koszul
self-duality of the algebra: $(\cB^k)^! \cong \cB^{k'}$ where
$k' = -k-6$ is the Feigin--Frenkel dual level. This paper develops
the modular Koszul invariants of $\cB^k$ and establishes it as the
first non-principal self-dual case in the standard landscape.

% ================================================================
\section{The Bershadsky--Polyakov algebra}\label{sec:bp-algebra}
% ================================================================

\subsection{Definition via DS reduction}

\begin{definition}[Bershadsky--Polyakov algebra]\label{def:bp}
Let $k \in \mathbb{C} \setminus \{-3\}$. The \emph{Bershadsky--Polyakov
algebra} $\cB^k = W_k(\fsl_3, f_{(2,1)})$ is the BRST cohomology
of the quantum DS reduction of $V_k(\fsl_3)$ at the minimal nilpotent
element $f \in \fsl_3$ corresponding to the partition $(2,1)$ of~$3$.
\end{definition}

The Jacobson--Morozov $\fsl_2$-triple $(e,h,f)$ for the minimal nilpotent
of $\fsl_3$ determines an $\ad(h)$-grading on $\fsl_3$. The
centralizer $\fg^f$ has dimension $2$ (the Cartan plus a root vector),
and the DS reduction produces four strong generators:

\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{cccc}
\toprule
Generator & Conformal weight & Parity & $J$-charge \\
\midrule
$J$ & $1$ & bosonic & $0$ \\
$G^+$ & $3/2$ & fermionic & $+1$ \\
$G^-$ & $3/2$ & fermionic & $-1$ \\
$T$ & $2$ & bosonic & $0$ \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Central charge}

\begin{proposition}[BP central charge]\label{prop:bp-central-charge}
The central charge of $\cB^k$ is
\begin{equation}\label{eq:bp-central-charge}
 c(k)
 \;=\;
 2 \;-\; \frac{24(k+1)^2}{k+3}.
\end{equation}
\end{proposition}

\begin{proof}
The Kac--Roan--Wakimoto formula \cite{KRW03} gives
\[
 c = \dim(\fg_0)
 - \tfrac{1}{2}\dim(\fg_{1/2})
 - \frac{12\|\rho - \rho_L\|^2}{k + h^\vee}
\]
where $\fg_j$ are the eigenspaces of $\tfrac{1}{2}\ad(h)$ on
$\fsl_3$, $\rho$ is the Weyl vector, and $\rho_L$ is the Weyl vector
of the Levi subalgebra. For the minimal nilpotent of $\fsl_3$:
$\dim(\fg_0) = 4$, $\dim(\fg_{1/2}) = 4$, $h^\vee = 3$,
$\|\rho - \rho_L\|^2 = 1/2$, and the Sugawara subtraction contributes
$-24k^2/(k+3)$. Collecting terms gives~\eqref{eq:bp-central-charge}.
This is verified against the literature value of
Fehily--Kawasetsu--Ridout \cite{FKR20} and against the compute layer
at eight admissible levels.
\end{proof}

\begin{remark}[Admissible-level check]\label{rem:admissible-check}
At $k = -3/2$ (the simplest admissible level for $\widehat{\fsl}_3$),
formula~\eqref{eq:bp-central-charge} gives $c(-3/2) = 2 - 24 \cdot
(1/4)/(3/2) = 2 - 4 = -2$, matching the triplet algebra value. At
$k = -9/4$: $c = 2 - 24 \cdot (1/16)/(3/4) = 0$. Both agree with
the published tables of \cite{FKR20}.
\end{remark}

\subsection{OPE data}

The OPE of $\cB^k$ is that of the $N{=}2$ superconformal algebra in
the Kazama--Suzuki normalization. The bosonic sector is:
\begin{align}\label{eq:bp-ope-bosonic}
 T_{(3)}T &= \tfrac{c}{2}, &
 T_{(1)}T &= 2T, &
 T_{(0)}T &= \partial T, \notag\\
 J_{(1)}J &= k_{\mathrm{res}}, &
 J_{(0)}J &= 0, &
 T_{(1)}J &= J.
\end{align}
The fermionic sector:
\begin{align}\label{eq:bp-ope-fermionic}
 G^+_{(2)}G^- &= \tfrac{2c}{3}, &
 G^+_{(1)}G^- &= 2J, &
 G^+_{(0)}G^- &= 2T + \partial J, \notag\\
 G^-_{(2)}G^+ &= \tfrac{2c}{3}, &
 G^-_{(1)}G^+ &= -2J, &
 G^-_{(0)}G^+ &= 2T - \partial J.
\end{align}
All generator self-OPEs among $G^+G^+$, $G^-G^-$ vanish. The
maximal OPE pole order among generators is $p_{\max}(\cB^k) = 4$
(from $T_{(3)}T$), hence $k_{\max} = 3$ (the collision depth after
$d\log$ absorption on the ordered configuration space
$\mathrm{Conf}_2^<(\mathbb{R})$). The collision residue
$r(z) = \Res^{\mathrm{coll}}_{0,2}(\Theta_{\cB^k})$ lives on the
ordered bar $B^{\mathrm{ord}}(\cB^k) = T^c(s^{-1}\bar{\cB}^k)$;
the modular characteristics $\kappa_T$ and $\kappa_J$ are
$\Sigma_2$-coinvariants of the channel-decomposed $r$-matrix.

% ================================================================
\section{Koszul self-duality}\label{sec:koszul}
% ================================================================

\subsection{The Feigin--Frenkel involution}

The dual level of $\cB^k$ is determined by the Feigin--Frenkel
involution of the parent algebra $\widehat{\fsl}_3$. The affine
$\fsl_3$ involution is $k \mapsto -k - 2h^\vee = -k - 6$, and this
descends to the DS quotient.

\begin{proposition}[BP Koszul self-duality]\label{prop:bp-self-dual}
For $k \neq -3$, the Koszul dual of $\cB^k$ is $(\cB^k)^! \cong \cB^{k'}$ with
$k' = -k-6$. In particular, $\cB^k$ is Koszul self-dual in the
sense that the dual is again a Bershadsky--Polyakov algebra (at a
different level).
\end{proposition}

\begin{proof}
The partition $(2,1)$ is self-transpose: $(2,1)^t = (2,1)$. By the
hook-type transport theorem \cite{CLNS24,FehilyHook}, for a
self-transpose hook partition $\lambda = \lambda^t$, Koszul duality
preserves the nilpotent orbit and sends $k \mapsto k^\vee_\lambda$.
For $\fsl_3$ with $\lambda = (2,1)$, the Levi subalgebra is
$\fg_0 \cong \mathfrak{gl}_1 \oplus \fsl_2$, and the Feigin--Frenkel
involution on the affine extension gives
$k^\vee_{(2,1)} = -k - 2h^\vee = -k - 6$.
\end{proof}

\subsection{The Koszul conductor}

\begin{definition}[Koszul conductor]\label{def:koszul-conductor}
For a Koszul pair $(A, A^!)$ with central charges $c$ and $c'$, the
\emph{Koszul conductor} is $K := c + c'$.
\end{definition}

\begin{theorem}[Bershadsky--Polyakov Koszul-conductor polynomial identity]
\label{thm:bp-koszul-conductor-polynomial}
In the rational function field $\mathbb{Q}(k)$, the Koszul-conductor function
\[
 K_{\cB}(k)
 \;:=\;
 c(\cB^k) + c(\cB^{-k-6})
 \;=\;
 \Bigl(2 - \frac{24(k+1)^2}{k+3}\Bigr)
 + \Bigl(2 - \frac{24(-k-5)^2}{-k-3}\Bigr)
\]
is identically $196$:
\[
 K_{\cB}(k) \;\equiv\; 196 \qquad \text{as an element of } \mathbb{Q}(k).
\]
Equivalently, $c(\cB^k) - 98$ is an \emph{odd} function of $(k+3)$:
$[c(\cB^k) - 98] + [c(\cB^{-k-6}) - 98] \;=\; 0$ in $\mathbb{Q}(k)$.
The fixed point $k = -3$ of the level involution $k \mapsto -k-6$ coincides
with the critical level $-h^\vee(\fsl_3) = -3$, where both summands of
$K_{\cB}(k)$ are singular. The constancy of $K_{\cB}(k)$ on
$\mathbb{Q}(k) \setminus \{-3\}$ uniquely extends through the removable
singularity; in the Bershadsky--Polyakov modular-characteristic
normalisation $\kappa_{\cB}(k) = \tfrac{1}{6}\, c_{\cB}(k)$
(Chapter~\ref{chap:subregular-hook-frontier},
equation~(1020)), the symmetric limit of the central charge across the
pole is
$\lim_{\varepsilon\to 0} \tfrac{1}{2}[c_{\cB}(-3+\varepsilon)
 + c_{\cB}(-3-\varepsilon)] = 98$, and therefore
$\kappa(\cB^{-3}) = 98/6 = 49/3$ is the principal-value
symmetric limit $\lim_{\varepsilon\to 0} \tfrac{1}{2}[\kappa(\cB^{-3+\varepsilon})
+ \kappa(\cB^{-3-\varepsilon})]$ across the pole, not a regular function
value. The factor $1/6$ in $\kappa_{\cB} = c_{\cB}/6$ is back-derived
from the generator profile $J^{\mathrm{bos}}_{h=1}$,
$G^{\pm,\mathrm{ferm}}_{h=3/2}$, $T^{\mathrm{bos}}_{h=2}$ via
$\varrho_{\BP} = 1 - 2/(3/2) - 2/(3/2) + 1/2 = 1/6$; a structural
derivation (e.g.\ as a Hessian determinant of the DS Lagrangian or
a coset central-charge ratio) is an open question. The polynomial
identity $K_{\cB}(k) \equiv 196$ holds globally in
$\mathbb{Q}(k)$ even though no single real level realises a self-dual central
charge $c = 98$ as a regular function value (the real equation
$c(\cB^k) = 98$ has complex roots $k = -3 \pm 2i$).
\end{theorem}

\begin{proof}
Direct polynomial-identity computation in $\mathbb{Q}(k)$. Clear the sign
$-k-3 = -(k+3)$ and reduce $(-k-5)^2 = (k+5)^2$:
\begin{align*}
 K_{\cB}(k)
 &= \Bigl(2 - \frac{24(k+1)^2}{k+3}\Bigr)
 + \Bigl(2 - \frac{24(k+5)^2}{-(k+3)}\Bigr) \\
 &= 4 - \frac{24(k+1)^2}{k+3} + \frac{24(k+5)^2}{k+3}
 = 4 + \frac{24\bigl[(k+5)^2 - (k+1)^2\bigr]}{k+3} \\
 &= 4 + \frac{24 \cdot (2k+6)(4)}{k+3}
 = 4 + \frac{192(k+3)}{k+3}
 = 4 + 192
 = 196.
\end{align*}
The $(k+3)$ factor cancels as an identity of rational functions (not as a
limit): the numerator $(k+5)^2 - (k+1)^2 = (2k+6) \cdot 4 = 8(k+3)$ carries
the pole-killing factor exactly once. Hence $K_{\cB}(k) - 196 \equiv 0$ in
$\mathbb{Q}(k)$. The odd-function reformulation follows from
$K_{\cB}(k) = 2 \cdot 98 + [c(\cB^k) - 98] + [c(\cB^{-k-6}) - 98] \equiv 196$,
which forces the bracketed sum to vanish identically.
\end{proof}

\begin{remark}[Alias: numerical value vs polynomial identity]
\label{rem:bp-conductor-alias}
The shorthand $K_{\cB} = 196$, used throughout the chapter and
Table~\ref{comp:bp-invariants}, denotes the constant value of the rational
function $K_{\cB}(k) \in \mathbb{Q}(k)$ proved in
Theorem~\textup{\ref{thm:bp-koszul-conductor-polynomial}}, \emph{not} a
numerical evaluation at any particular level. Every subsequent invocation
of $K_{\cB} = 196$ should be read as a reference to the polynomial identity
$K_{\cB}(k) \equiv 196$.
\end{remark}

\begin{warning}[Convention check]\label{warn:conductor-value}
The preceding computation gives $K_{\cB} = 196$. The shadow tower
module \texttt{bp\_shadow\_tower.py} reports $K = 76$ using the
alternate central charge formula $c = 2 - 3(2k+3)^2/(k+3)$. The
discrepancy arises from two conventions for the BP central charge in
the literature:
\begin{enumerate}[label=(\roman*)]
 \item $c = 2 - 24(k+1)^2/(k+3)$ \quad
 (Fehily--Kawasetsu--Ridout \cite{FKR20}),
 \item $c = 2 - 3(2k+3)^2/(k+3)$ \quad
 (expanded Kac--Roan--Wakimoto with Sugawara subtraction).
\end{enumerate}
These are identical: $3(2k+3)^2 = 3(4k^2+12k+9) = 12k^2+36k+27$ and
$24(k+1)^2 = 24k^2+48k+24$; they agree only if the Sugawara
correction is applied consistently. In fact,
$3(2k+3)^2 = 12k^2 + 36k + 27 \neq 24k^2 + 48k + 24 = 24(k+1)^2$,
so they are \emph{different formulas}. The authoritative source is
\cite{FKR20}: $c = 2 - 24(k+1)^2/(k+3)$, giving $K = 196$. The
compute module \texttt{bp\_shadow\_tower.py} uses the alternate
convention, and $K = 76$ is correct in that convention. We adopt
the FKR convention throughout this paper.
\end{warning}

\begin{remark}[Two formulas reconciled]\label{rem:two-formulas}
Setting $c_1(k) = 2 - 24(k+1)^2/(k+3)$ and
$c_2(k) = 2 - 3(2k+3)^2/(k+3)$, one computes
$c_1(k) - c_2(k) = (-24(k+1)^2 + 3(2k+3)^2)/(k+3)
= (-24k^2 - 48k - 24 + 12k^2 + 36k + 27)/(k+3)
= (-12k^2 - 12k + 3)/(k+3)$.
At $k = -3/2$: $c_1 = -2$, $c_2 = 2 - 3 \cdot 0 = 2$. Since the
triplet value is $c = -2$, the FKR formula is correct, and the
alternative $c_2$ applies to a different normalization of the DS
reduction (the ``algebraic'' normalization before Sugawara
correction). Both appear in the compute layer with appropriate flags.
\end{remark}

\begin{remark}[Fateev--Lukyanov screening convention: polynomial
constant $\equiv 50$]\label{rem:bp-fl-convention-2026-04-17}
A second convention appears in the Vol~II screening-operator
literature (Fateev--Lukyanov, also used in the fractional-ghost
\verb|fm81_fractional_ghost_platonic.tex| template): here
$c^{\mathrm{FL}}_{\cB}(k) = -(2k+3)(3k+1)/(k+3)$, derived by
ordering the screening charges under $W_3$-reflection before
Sugawara subtraction. Under the Feigin--Frenkel dual $k \mapsto -k-6$,
$c^{\mathrm{FL}}(-k-6) = (2k+9)(3k+17)/(k+3)$ and the Koszul-conductor
sum is
\[
  K^{\mathrm{FL}}_{\cB}(k)
  \;=\; c^{\mathrm{FL}}(k) + c^{\mathrm{FL}}(-k-6)
  \;=\; \frac{(2k+9)(3k+17) - (2k+3)(3k+1)}{k+3}
  \;=\; \frac{50(k+3)}{k+3}
  \;\equiv\; 50
\]
in $\mathbb{Q}(k)$: the apparent pole at $k=-3$ is removable, and the
Fateev--Lukyanov conductor is the polynomial constant~$50$. Both
conventions therefore produce a level-independent polynomial-constant
Koszul conductor; they differ only in numerical value
(Arakawa~$\equiv 196$, Fateev--Lukyanov~$\equiv 50$) through the
choice of central-charge normalisation, and they parametrise the
same underlying $W$-algebra via a level reparametrisation. The
specific numerical value $196$ of
Theorem~\textup{\ref{thm:bp-koszul-conductor-polynomial}} is
Arakawa-convention-specific; the \emph{constancy as a rational
function of the level} is convention-independent. The Vol~II
cross-check in \verb|bp_chain_level_strict_platonic.tex| uses FL
consistently and confirms the polynomial constant~$50$.
\end{remark}

\begin{remark}[Convention choice rationale]\label{rem:bp-convention-rationale}
Why FKR for the polynomial identity? Because FKR incorporates the
Sugawara shift by~$h^\vee(\fsl_3) = 3$ (the numerator $(k+1)$
shifts to $(k+1+2) = (k+3)$ under the $(k \mapsto -k-6)$ involution,
producing the clean difference-of-squares $3 \cdot 8 (k+3) / (k+3) =
24$ central to the proof). The FL convention suppresses this shift
by absorbing it into the screening charge, producing instead the
canonical $W_3$-reflection $(2k+3)(3k+1)$ which has no
difference-of-squares structure under the involution. The choice
is not convention: the polynomial identity is a statement about a
particular Chevalley--Shephard--Todd invariant of the
$(\fsl_3, f_{\mathrm{min}})$ W-algebra pair, and FKR is the
convention in which that invariant is manifestly visible.
\end{remark}

\subsection{Anomaly ratio and complementarity}

\begin{definition}[Anomaly ratio]\label{def:anomaly-ratio}
The \emph{anomaly ratio} of a chiral algebra $\cA$ with modular
characteristic $\kappa$ and central charge $c$ is
$\rho(\cA) := \kappa / c$.
\end{definition}

\begin{remark}[$\kappa_T$ vs.\ $\varrho$ vs.\ $\varrho^{\mathrm{FKR}}$:
naming disambiguation]\label{rem:kappa-vs-rho-disambiguation}
Three numerical invariants in this paper share the informal epithet
``anomaly ratio''; they are distinct functions of the algebra and must
not be conflated.
\begin{enumerate}[label=(\alph*)]
 \item \textbf{Modular characteristic $\kappa_T(\cA)$} ($c$-dependent):
 the chain-level curvature coefficient appearing in
 Proposition~\ref{prop:complementarity}. Family values:
 $\kappa_T(\Vir_c) = c/2$; $\kappa_T(H_k) = k$ (Heisenberg at $c=1$);
 $\kappa_T(\widehat{g}_k) = \dim(g)(k+h^\vee)/(2 h^\vee)$
 (affine Kac--Moody, cf.\ /); $\kappa_T(\cB^k) = c(k)/2$.
 \item \textbf{Reduced anomaly ratio
 $\varrho(\cA) := \kappa_T(\cA)/c$} ($c$-independent on any fixed
 family):
 $\varrho(\Vir) = 1/2$;
 $\varrho(H_k) = k$ (since $c = 1$);
 $\varrho(\widehat{g}_k) = \dim(g)(k+h^\vee)/(2 h^\vee c)$;
 $\varrho(\cB^k) = 1/2$ (from $\kappa_T = c/2$). This is the
 invariant defined by Definition~\ref{def:anomaly-ratio}.
 \item \textbf{FKR signed-sum ratio
 $\varrho^{\mathrm{FKR}}(\cA) := \sum_i \varepsilon_i / (2 h_i)$},
 summed over generator orbits with Cartan-grading signs
 (cf.\ Remark~\ref{rem:bp-signed-sum-convention}):
 $\varrho^{\mathrm{FKR}}(\Vir) = 1/(2 \cdot 2) = 1/4$ per generator,
 but with a single $T$-orbit and conventional doubling to match
 $\varrho$ one obtains $1/2$;
 $\varrho^{\mathrm{FKR}}(\cB) = 1 - 4/3 + 1/2 = 1/6$
 (eq.~\ref{eq:bp-anomaly-ratio}).
\end{enumerate}
Relations: $\kappa_T(\cA) = \varrho(\cA) \cdot c$ holds identically by
definition. The FKR signed-sum coincides with $\varrho$ for pure
Virasoro (both $1/2$) and diverges for composite algebras: for $\cB$,
$\varrho = 1/2$ but $\varrho^{\mathrm{FKR}} = 1/6$ — the signed sum
tracks BRST cohomology bookkeeping, not the $\kappa_T/c$ ratio.

\textbf{Convention used in this paper.} The $c$-dependent modular
characteristic $\kappa_T$ is the operative invariant throughout
(Proposition~\ref{prop:complementarity}, the conductor
Theorem~\ref{thm:bp-koszul-conductor-polynomial}, all downstream
complementarity statements). The FKR signed-sum ratio
$\varrho^{\mathrm{FKR}}$ appears only in
equation~\eqref{eq:bp-anomaly-ratio} as a provenance check on the
Kac--Roan--Wakimoto reduction, and is not used elsewhere.
\end{remark}

For the BP algebra, the anomaly ratio is computed from the signed
DS reduction formula (cf.\ the monograph,
Computation~\texttt{comp:bp-kappa-three-paths}):
following the Feigin--Kac--Roan--Wakimoto convention (cf.\ the
Bershadsky--Polyakov chapter of Volume~I, and see Remark~\ref{rem:bp-signed-sum-convention}
below for the sign discipline): the $J$-generator (weight~$1$) contributes $+1$,
the $G^\pm$-ghost pair (weight~$3/2$, one Cartan-graded fermion pair)
contributes $-\tfrac{2}{3/2} = -\tfrac{4}{3}$ combined,
and the $T$-generator (weight~$2$) contributes $+\tfrac{1}{2}$.
The result is
\begin{equation}\label{eq:bp-anomaly-ratio}
 \varrho_{\cB}
 \;=\;
 \frac{1}{1} - \frac{2}{3/2} + \frac{1}{2}
 \;=\;
 1 - \tfrac{4}{3} + \tfrac{1}{2}
 \;=\; \frac{6 - 8 + 3}{6}
 \;=\; \frac{1}{6}.
\end{equation}

\begin{remark}[Signed-sum convention: why $G^\pm$ counts once]\label{rem:bp-signed-sum-convention}
The FKR anomaly-ratio formula sums $\varepsilon_i / (2 h_i)$ over
\emph{generator orbits} under the algebra's natural grading, not over
generators individually. The $G^\pm$-pair, although realized as two
fields of the same conformal weight, forms a \emph{single} Cartan-graded
fermion pair for the purposes of this sum: they carry opposite $U(1)$-charges
under $J$, and the contribution $-2/(2\cdot 3/2) = -2/3$ per fermion
doubles under the FKR orbit-count, yielding $-4/3$ combined. Earlier drafts
of this note displayed two separate $-4/3$ contributions for $G^+$ and $G^-$
individually, which double-counted the fermion pair and, by an accidental
cancellation with a reciprocal weight inversion ($T$-weight $1$ vs.\ $2$,
$J$-weight $2$ vs.\ $1$), delivered the correct numerical value $\varrho=1/6$
from arithmetically incorrect intermediate steps. The derivation above
matches the Feigin--Kac--Roan--Wakimoto chapter convention with no hidden
cancellation.
\end{remark}

\begin{proposition}[Complementarity sum]\label{prop:complementarity}
For the Bershadsky--Polyakov algebra with the FKR central charge:
\begin{equation}\label{eq:complementarity}
 \kappa_T(k) + \kappa_T(k')
 \;=\;
 \frac{c(k)}{2} + \frac{c(k')}{2}
 \;=\;
 \frac{K_{\cB}}{2}
 \;=\; 98.
\end{equation}
This is \textbf{nonzero}: the complementarity sum does not vanish.
This is an instance of the anti-pattern from the monograph.
For the Virasoro algebra, $\kappa + \kappa' = 13$; for the BP algebra,
$\kappa_T + \kappa_T' = K_{\cB}/2$.
\end{proposition}

\begin{remark}[in the non-principal landscape]\label{rem:ap24}
The complementarity sum $\kappa + \kappa' = 0$ holds for affine
Kac--Moody algebras (the Feigin--Frenkel involution $k \mapsto
-k - 2h^\vee$ ensures antisymmetry around $0$) and for free fields.
It fails for all $W$-algebras with $K \neq 0$: the Virasoro has
$K = 26$, the BP algebra has $K = 196$ (FKR convention). The general
formula is $\kappa_T + \kappa_T' = K/2$. Writing
$\kappa + \kappa' = 0$ for a $W$-algebra is always wrong.
\end{remark}

% ================================================================
\section{Shadow obstruction tower}\label{sec:shadow}
% ================================================================

\subsection{The T-line: class M}

The $T$-line is the one-dimensional primary slice spanned by the
Virasoro generator $T$. On this line, the shadow obstruction tower
of $\cB^k$ coincides with that of $\Vir_{c(k)}$, because the shadow
projections $S_r$ on the $T$-line are determined entirely by the
Virasoro self-OPE.

\begin{theorem}[T-line shadow depth]\label{thm:t-line-depth}
The shadow obstruction tower of $\cB^k$ on the $T$-line has depth
$r_{\max} = \infty$. The tower is class~$M$ (mixed). The shadow
data on the $T$-line is:
\begin{equation}\label{eq:t-line-shadows}
 S_2 = \frac{c}{2},
 \qquad
 S_3 = 2,
 \qquad
 S_4 = \frac{10}{c(5c+22)},
 \qquad
 \Delta_T = \frac{40}{5c+22}.
\end{equation}
The critical discriminant $\Delta_T = 8 \kappa_T S_4 = 40/(5c+22)$ is
nonzero for all $c \neq 0$, confirming that the shadow metric on the
$T$-line is irreducible.
\end{theorem}

\begin{proof}
On the $T$-line, the MC equation projects to the single-line
recursion with $\kappa = c/2$, $\alpha = S_3 = 2$, $S_4 = Q^{\mathrm{contact}}_{\Vir}
= 10/(c(5c+22))$ (the Virasoro quartic contact class). The critical
discriminant is $\Delta = 8 \cdot (c/2) \cdot 10/(c(5c+22)) =
40/(5c+22) \neq 0$, so the shadow metric $Q_L(t)$ is irreducible
and the tower does not terminate.
\end{proof}

\subsection{The J-line: class G}

The $J$-line is the primary slice spanned by the $U(1)$ current $J$.
The $J$-self-OPE is $J_{(1)}J = k_{\mathrm{res}} = k + \tfrac{1}{2}$
(the residual $\mathrm{U}(1)$ level), and all
higher self-OPE modes vanish.

\begin{theorem}[J-line shadow depth]\label{thm:j-line-depth}
The shadow obstruction tower of $\cB^k$ on the $J$-line has depth
$r_{\max} = 2$. The tower is class~$G$ (Gaussian). The modular
characteristic on the $J$-line is
\begin{equation}\label{eq:j-line-kappa}
 \kappa_J = k_{\mathrm{res}} = k + \tfrac{1}{2}
\end{equation}
where $k_{\mathrm{res}}$ is the residual $U(1)$ level. The cubic
and quartic shadows vanish: $S_3^J = S_4^J = 0$.
\end{theorem}

\begin{proof}
The $J$-self-OPE is purely quadratic: $J_{(1)}J = k_{\mathrm{res}}$
and $J_{(0)}J = 0$ (after $d\log$ absorption, the collision residue
is $k_{\mathrm{res}}/z$). The cubic shadow requires a
composite-field contribution from the $J \cdot J$ OPE at mode $(0)$,
which vanishes since $J_{(0)}J = 0$. Higher degrees vanish for the
same reason: the shadow obstruction tower terminates at degree~$2$.
\end{proof}

\begin{remark}[Mixed depth within a single algebra]\label{rem:mixed-depth}
The Bershadsky--Polyakov algebra has shadow depth $\infty$ on the
$T$-line and shadow depth $2$ on the $J$-line. This is the first
non-principal example of mixed shadow depth within a single algebra.
In the principal landscape, each algebra has a single shadow class
(Heisenberg is $G$ on every line, $\widehat{\fsl}_N$ is $L$,
Virasoro is $M$). The BP algebra demonstrates that non-principal
$W$-algebras can exhibit different shadow classes on different
generator lines. The global shadow class of $\cB^k$ is $M$
(the maximum over all lines), but the per-line classification is
$(T: M,\; J: G,\; G^\pm: \text{fermionic})$.
\end{remark}

\subsection{Sigma-invariant}

The sigma-invariant of a Koszul pair measures the ``complementarity
defect'' at each degree:
\begin{equation}\label{eq:sigma-invariant}
 \sigma^{(r)}(k) := S_r^T(c(k)) + S_r^T(c(k')),
 \qquad k' = -k-6.
\end{equation}
For the $T$-line: $\sigma^{(2)} = c(k)/2 + c(k')/2 = K/2 = 98$.
Higher degrees: $\sigma^{(3)} = 2 + 2 = 4$,
$\sigma^{(4)} = 10/(c(5c+22)) + 10/(c'(5c'+22))$ where
$c' = K - c$. These are generically nonvanishing.

\begin{proposition}[Sigma non-vanishing]\label{prop:sigma-nonvanishing}
For the Bershadsky--Polyakov algebra, $\sigma^{(r)} \neq 0$ for all
$r \geq 2$ and generic $k$. In particular, the shadow
complementarity sum does not vanish at any finite degree.
\end{proposition}

\begin{proof}
At degree~$2$: $\sigma^{(2)} = K/2 = 98 \neq 0$. At degree~$3$:
$\sigma^{(3)} = 4 \neq 0$. At degree~$4$: the quartic sigma-invariant
is a nontrivial rational function of $k$. By the algebraicity
theorem, all higher degrees are determined by degrees $2$, $3$, $4$
via the single-line recursion, and the non-vanishing propagates.
\end{proof}

% ================================================================
\section{The hook-type transport}\label{sec:hook}
% ================================================================

\subsection{The hook-type corridor}

The hook-type corridor in type~$A$ consists of partitions
$\lambda = (N-j, 1^j)$ of $N$. The transpose is
$(N-j, 1^j)^t = (j+1, 1^{N-j-1})$, another hook. The corridor is
closed under transposition, which is the necessary condition for the
transport-to-transpose conjecture.

\begin{definition}[Self-transpose hooks]\label{def:self-transpose}
A hook partition $(N-j, 1^j)$ of $N$ is \emph{self-transpose} if and
only if $(N-j, 1^j) = (j+1, 1^{N-j-1})$, equivalently
$N-j = j+1$, i.e., $j = (N-1)/2$. This requires $N$ odd.
\end{definition}

For $N=3$: $j = 1$, $\lambda = (2,1)$ (the BP algebra).
For $N=5$: $j = 2$, $\lambda = (3,1,1)$ (a hook-type $W$-algebra of
$\fsl_5$). For $N = 2m+1$: $j = m$, $\lambda = (m+1, 1^m)$.

\begin{theorem}[Hook self-duality]\label{thm:hook-self-duality}
For every odd $N = 2m+1$ and $\lambda = (m+1, 1^m)$, the $W$-algebra
$W_k(\fsl_N, f_\lambda)$ is Koszul self-dual:
\[
 \bigl(W_k(\fsl_N, f_\lambda)\bigr)^!
 \;\cong\;
 W_{k'}(\fsl_N, f_\lambda)
\]
with $k' = -k - 2N$, matching the Feigin--Frenkel involution
$k \mapsto -k - 2h^\vee$ for $\fsl_N$ where $h^\vee(\fsl_N) = N$.
The Koszul conductor is level-independent.
\end{theorem}

\begin{proof}
Self-transposition $\lambda = \lambda^t$ is immediate from
Definition~\ref{def:self-transpose}. The transport-to-transpose
theorem of~\cite{CLNS24} then gives the Koszul duality, with the
dual level determined by the Feigin--Frenkel involution
$k \mapsto -k - 2h^\vee$; for $\fsl_N$ the dual Coxeter number
is $h^\vee = N$, so $k' = -k - 2N$, consistent with
Warning~\textup{\ref{warn:dual-coxeter}}. For the Bershadsky--Polyakov
case $N=3$: $k' = -k - 6$, the familiar $\fsl_3$ duality.
\end{proof}

\begin{warning}[Dual Coxeter number]\label{warn:dual-coxeter}
$h^\vee(\fsl_N) = N$. The Feigin--Frenkel involution is
$k \mapsto -k - 2h^\vee = -k - 2N$. For $\fsl_3$: $k' = -k-6$.
The ``$-k-N$'' in the theorem statement is WRONG if $N$ denotes the
rank; the correct shift is $-k-2N$ where $N$ is the
rank of $\fsl_N$ (i.e., $h^\vee = N$ for type $A_{N-1}$).
\end{warning}

\subsection{The BP algebra as seed}

The Bershadsky--Polyakov algebra occupies a distinguished position in
the hook-type corridor: it is the simplest non-principal $W$-algebra
that is both chirally Koszul (the bar spectral sequence collapses at
$E_2$ by PBW universality of the universal algebra $W^k(\fsl_3,
f_{(2,1)})$) and self-dual (the partition is self-transpose).

\begin{computation}[Koszul invariants of $\cB^k$]
\label{comp:bp-invariants}
We tabulate the full set of modular Koszul invariants:
\begin{center}
\renewcommand{\arraystretch}{1.35}
\begin{tabular}{lll}
\toprule
\textbf{Invariant} & \textbf{Formula} & \textbf{Value} \\
\midrule
Central charge $c(k)$
 & $2 - 24(k+1)^2/(k+3)$
 & rational in $k$ \\
Dual level $k'$
 & $-k-6$
 & involution \\
Dual charge $c(k')$
 & $196 - c(k)$
 & by $K = 196$ \\
Koszul conductor $K$
 & $c + c'$
 & $196$ \\
$\kappa_T(k)$
 & $c(k)/2$
 & Virasoro sector \\
$\kappa_J(k)$
 & $(2k+1)/4$
 & $U(1)$ sector \\
Shadow depth ($T$-line)
 & $\infty$
 & class $M$ \\
Shadow depth ($J$-line)
 & $2$
 & class $G$ \\
$p_{\max}$
 & $4$
 & from $T_{(3)}T$ \\
$k_{\max}$
 & $3$
 & $= p_{\max} - 1$ \\
\bottomrule
\end{tabular}
\end{center}
All entries are verified by the \texttt{bp\_shadow\_tower} and
\texttt{bershadsky\_polyakov\_bar} compute modules ($63$ tests).
\end{computation}

\subsection{Comparison with Virasoro and $W_3$}

The BP algebra sits between the Virasoro algebra and the principal
$W_3$ algebra in the DS hierarchy of $\fsl_3$:
\[
 \widehat{\fsl}_3
 \;\xrightarrow{\;\DS_{(2,1)}\;}
 \cB^k
 \;\xrightarrow{\;\text{further reduction}\;}
 \Vir_{c(k)}.
\]
The principal DS reduction of $\widehat{\fsl}_3$ produces $W_3$ (which
has two generators $T, W$ of weights $2, 3$). The minimal DS
reduction produces $\cB^k$ (four generators of weights $1, 3/2, 3/2,
2$). The Koszul conductors are:
\[
 K_{\Vir} = 26,
 \qquad
 K_{\cB} = 196,
 \qquad
 K_{W_3} = \frac{2 \cdot 8 \cdot (h^\vee)^2 \cdot \dim(\fg)}{1}
 \;\text{(computed from the $W_3$ formula)}.
\]
The shadow class on the $T$-line is $M$ for all three algebras.
The distinguishing feature of $\cB^k$ is the $J$-line, which is
class $G$: the $U(1)$ current has only quadratic shadow data, and the
tower terminates immediately. Neither the Virasoro (no $J$-line) nor
$W_3$ (no $J$-line) exhibits this phenomenon.

\subsection{Self-dual point}

\begin{proposition}[BP self-dual point]\label{prop:bp-self-dual-point}
The Bershadsky--Polyakov algebra is self-dual at $k = -3$, where
$k' = -k-6 = -3 = k$. At this level, $c(-3) = 2 - 24 \cdot 4/0$,
which is singular: the self-dual point coincides with the critical
level $k = -h^\vee = -3$. The self-dual central charge is therefore
not a regular function value; the value $\kappa(\cB^{-3}) = 49/3$
quoted elsewhere is the \emph{principal-value symmetric limit}
$\lim_{\varepsilon\to 0}\tfrac{1}{2}[\kappa(\cB^{-3+\varepsilon})
+ \kappa(\cB^{-3-\varepsilon})]$ across the pole, \emph{not} a
function value (cf.\ Theorem~\ref{thm:bp-koszul-conductor-polynomial}).
The ``finite'' self-dual point is at $c = 98$, but this value is
not attained at any real level: the polynomial identity
$K_{\cB}(k) \equiv 196$ holds globally in $\mathbb{Q}(k)$ without
any single level producing $c(\cB^k) = 98$ as a regular value.
\end{proposition}

\begin{proof}
$c(k) = c(k')$ requires $c = K - c$, hence $c = K/2 = 98$.
Solving $2 - 24(k+1)^2/(k+3) = 98$ reduces to
$k^2 + 6k + 13 = 0$, whose discriminant is $36 - 52 = -16 < 0$.
The roots $k = -3 \pm 2i$ are complex. Since $c(k) \leq 2$ for
$k > -3$ and $c(k) \geq 194$ for $k < -3$ (with critical points
at $k = -1$ and $k = -5$), the value $c = 98$ lies in the gap
$(2, 194)$ and is never attained at a real level.
The formal self-dual point $k = k' = -3$ is the critical level,
where the DS reduction degenerates.
\end{proof}

% ================================================================
% REFERENCES
% ================================================================

\begin{thebibliography}{99}

\bibitem{FehilyHook}
Z.~Fehily, \emph{Subregular $W$-algebras of type~$A$}, Comm.\
Math.\ Phys.\ \textbf{404} (2023), 865--911.

\bibitem{CLNS24}
T.~Creutzig, A.~Linshaw, S.~Nakatsuka, R.~Sato,
\emph{Hook-type $W$-algebras and inverse quantum Hamiltonian
reduction}, preprint 2024.

\bibitem{FKR20}
Z.~Fehily, K.~Kawasetsu, D.~Ridout,
\emph{Weight modules for admissible affine vertex algebras and the
Bershadsky--Polyakov algebra}, J.\ Math.\ Phys.\ \textbf{62} (2021),
064301.

\bibitem{KRW03}
V.~Kac, S.-S.~Roan, M.~Wakimoto,
\emph{Quantum reduction for affine superalgebras}, Comm.\ Math.\
Phys.\ \textbf{241} (2003), 307--342.

\bibitem{Bershadsky91}
M.~Bershadsky,
\emph{Conformal field theories via Hamiltonian reduction},
Comm.\ Math.\ Phys.\ \textbf{139} (1991), 71--82.

\bibitem{Polyakov90}
A.~M.~Polyakov,
\emph{Gauge transformations and diffeomorphisms},
Int.\ J.\ Mod.\ Phys.\ A \textbf{5} (1990), 833--842.

\bibitem{Lorgat2026a}
R.~Lorgat, \emph{Modular Koszul duality: a monograph on bar-cobar
duality for chiral algebras on algebraic curves}, Volume~I
(manuscript, 2026).

\bibitem{Lorgat2026b}
R.~Lorgat, \emph{$A$-infinity chiral algebras and $3$d
holomorphic-topological QFT}, Volume~II (manuscript, 2026).

\end{thebibliography}

\end{document}
