\documentclass[11pt]{article}
\usepackage[localtheorems]{raeez-math-template}

%%% Packages

%%% Page geometry

%%% Theorem environments
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{construction}[theorem]{Construction}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

%%% Macros
\newcommand{\fg}{\mathfrak{g}}
\newcommand{\fh}{\mathfrak{h}}
\newcommand{\fsl}{\mathfrak{sl}}
\newcommand{\Ran}{\mathrm{Ran}}
\newcommand{\Mbar}{\overline{\mathcal{M}}}
\newcommand{\FM}{\mathrm{FM}}
\newcommand{\MC}{\mathrm{MC}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cW}{\mathcal{W}}
\newcommand{\cZ}{\mathcal{Z}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\barB}{\overline{B}}
\newcommand{\Abar}{\bar{\cA}}
\newcommand{\Res}{\operatorname{Res}}
\newcommand{\disc}{\operatorname{disc}}
\newcommand{\ChirHoch}{\mathrm{ChirHoch}}
\newcommand{\Eone}{E_1}
\newcommand{\Einf}{E_\infty}
\newcommand{\gAmod}{\mathfrak{g}_{\cA}^{\mathrm{mod}}}
\newcommand{\Ahat}{\hat{A}}
\newcommand{\Confinf}{\mathrm{Conv}_\infty}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\av}{av}
\DeclareMathOperator{\Conf}{Conf}
\DeclareMathOperator{\obs}{obs}

%%% Title
\title{The five theorems of modular Koszul duality}
\author{Raeez Lorgat}
\date{}

\begin{document}
\maketitle

%%% ================================================================
%%% ABSTRACT
%%% ================================================================

\begin{abstract}
Koszul duality over a point terminates: a quadratic algebra
determines a dual coalgebra, the bar construction mediates
between them, and no further structure appears. Over an
algebraic curve, the theory does not terminate. The bar
differential acquires curvature from the Hodge bundle on
moduli space; its failure to square to zero is controlled
by a single scalar $\kappa(\cA)$, the modular
characteristic, extracted from the collision residue of the
universal Maurer--Cartan element.

The chiral algebra $\cA$ is the level-$1$ chart
$A_b = \mathrm{End}_{\mathcal{C}}(b)$ of a factorization
dg-category $\mathcal{C}^{\mathrm{op}}$ on a tangential log
curve $(X, D, \tau)$, evaluated at a vacuum object $b$. Five
theorems characterize the levels of the resulting Beilinson
tower
\[
 \mathcal{C}^{\mathrm{op}}
 \;\xrightarrow{b}\;
 A_b
 \;\xrightarrow{\barB}\;
 B(A_b)
 \;\xrightarrow{Z^{\mathrm{der}}_{\mathrm{ch}}}\;
 \text{bulk}
 \;\xrightarrow{}\;
 \text{line ops}
 \;\xrightarrow{\mathrm{tr}}\;
 \text{modular shadow}.
\]
Each theorem carries a type signature
(\emph{quadrant, presentation, level, hypothesis package}).

Theorem~A is a chiral Koszul reflection $K^2 \simeq \mathrm{id}$
on $\mathrm{Kosz}(X)$ at the chart-bar boundary $1 \leftrightarrow 2$,
under the augmented + complete + finite-dim graded
hypothesis package $(H1)$--$(H3)$, in three parametric strengths:
\emph{weak} (bar--cobar adjunction unconditional),
\emph{strong} ($K^2 \simeq \mathrm{id}$ on the Koszul locus),
\emph{strongest-rejected} (an unconditional equivalence on
$\mathrm{Alg}^{\mathrm{aug}}$ off the Koszul locus, false because
$L_0$-witnesses kill conilpotency outside the weight-completed
ambient).
Theorem~B inscribes bar--cobar inversion
$\Omega_X(\barB_X(C)) \xrightarrow{\sim} C$ in
$D^{\mathrm{co}}_{\mathrm{ch}}(X)$ at level $1 \to 3$, on the
Koszul locus, with the class-$\mathsf{M}$ chain-level statement
ambient-qualified to the weight-completed coderived target.
Theorem~C is the $5 \times 5$ $\kappa$-stratification matrix
on rows $\mathsf{G/L/C/M/B}$ with columns
$\{\kappa_{\mathrm{cat}},
\kappa^{\mathrm{Hodge}}_{\mathrm{ch}},
\kappa^{\mathrm{Heis}}_{\mathrm{ch}},
\kappa_{\mathrm{BKM}},
\kappa_{\mathrm{fiber}}\}$ at level $5$ per stratum;
$K3 \times E$ anchors row $\mathsf{B}$ at $(0,\,0,\,3,\,5,\,24)$,
and the Lagrangian decomposition controlling each row at the
ambient level forces the family-dependent complementarity sum
$\kappa(\cA) + \kappa(\cA^!)$ ($0$ for Kac--Moody and free
fields, $13$ for Virasoro).
Theorem~D identifies $\mathrm{obs}_g = \kappa \cdot \lambda_g$
as the universal scalar genus class on $\overline{\cM}_{g,n}$ at
level $4$, with genus-$1$ unconditional and the all-genera
statement on the scalar-diagonal uniform-weight lane proved by
Grothendieck--Riemann--Roch on the universal curve and by
clutching propagation independently.
Theorem~H proves $\mathrm{ChirHoch}^\bullet(A_b) \subset \{0,1,2\}$
at level $3$ on the Koszul locus, with class~$\mathsf{M}$ chain-level
statement requiring the completed / pro / $J$-adic ambient.

All five theorems are $\Sigma_n$-coinvariant projections of a
single $\Eone$ object: the ordered bar complex
$\barB^{\mathrm{ord}}_X(A_b)$ with its deconcatenation
coproduct and classical $R$-matrix $r_{A_b}(z)$. The averaging
map $\mathrm{av}\colon \mathfrak{g}^{E_1} \to \mathfrak{g}^{\mathrm{mod}}$
recovers $\kappa$ from $r$ on the abelian and scalar lanes;
the non-abelian Kac--Moody value $\kappa = \mathrm{av}(r) + \dim(\fg)/2$
encodes the Sugawara shift. The locus
$\mathrm{KSDual} \subset \mathrm{Kosz}(X)$ on which the Verdier
involution $\cA \mapsto \cA^!$ acts by the identity is the
$\mathbb{Z}/2$-fixed sublocus where Theorem~A is an equivalence,
Theorem~H is exact in $\{0,1,2\}$, and the universal trace
identity
$\kappa_{\mathrm{BKM}}(\Phi_N) = c_N(0)/2$
is the equivariant signature.
The Heisenberg algebra provides the complete base computation;
every other family is a variation with increasingly complex
collision residues.
\end{abstract}

\tableofcontents

%%% ================================================================
%%% SECTION 1: INTRODUCTION
%%% ================================================================

\section{Introduction: from a point to a curve}
\label{sec:introduction}

\subsection{The problem}

Koszul duality over a point terminates. A quadratic algebra
$A = T(V)/(R)$ determines a dual coalgebra
$A^{!} = (H^*(B(A)))^\vee$, the bar construction
$B(A) = (T^c(s^{-1}\bar{A}), d_B)$ mediates between them, and the
cobar functor inverts:
$\Omega(B(A)) \xrightarrow{\sim} A$ when $A$ is Koszul
\cite{Priddy70, BGS96, LV12}. The bar cohomology concentrates in
degree $1$, the derived categories of $A$-modules and
$A^!$-modules are equivalent, and no further structure appears.

Over an algebraic curve, three obstructions prevent this from
working. The generators of a chiral algebra are sections of a
$\cD_X$-module, not elements of a vector space. The relations are
operator product expansions with poles of arbitrary order, not
quadratic expressions. The topology of higher-genus curves forces
the fiberwise bar differential to satisfy
$d_{\mathrm{fib}}^2 = \kappa(\cA) \cdot \omega_g$ rather than
$d^2 = 0$, where $\omega_g = c_1(\mathbb{E})$ is the Hodge class
on $\Mbar_g$.

The question is: what structure replaces the terminating classical
theory?

\subsection{The answer}

The chiral algebra $\cA = A_b$ is the chart at a vacuum
$b \in \mathcal{C}^{\mathrm{op}}$ of a factorization dg-category
on a tangential log curve $(X, D, \tau)$. The Beilinson tower
$\mathcal{C}^{\mathrm{op}} \xrightarrow{b} A_b \xrightarrow{\barB}
B(A_b) \xrightarrow{Z^{\mathrm{der}}_{\mathrm{ch}}} \text{bulk}
\xrightarrow{} \text{line ops} \xrightarrow{\mathrm{tr}}
\text{modular shadow}$ organises the open quadrant of the
factorization theory; the five theorems characterise
its levels. The ordered bar complex
\begin{equation}\label{eq:bar-complex-def}
\barB^{\mathrm{ord}}_X(\cA)
\;=\;
T^c(s^{-1}\Abar),
\qquad
|s^{-1}v| = |v| - 1,
\end{equation}
with deconcatenation coproduct
\begin{equation}\label{eq:deconcatenation}
\Delta[s^{-1}a_1 | \cdots | s^{-1}a_n]
\;=\;
\sum_{i=0}^{n}
[s^{-1}a_1 | \cdots | s^{-1}a_i]
\otimes
[s^{-1}a_{i+1} | \cdots | s^{-1}a_n],
\end{equation}
is a cofree $\Eone$-coalgebra. Here
$\Abar = \ker(\varepsilon \colon \cA \to \omega_X)$ is the
augmentation ideal and $s^{-1}$ is the desuspension, lowering
degree by $1$. The integral kernel is the logarithmic $1$-form
\begin{equation}\label{eq:eta}
\eta_{12} \;=\; d\log(z_1 - z_2)
\;=\; \frac{dz_1 - dz_2}{z_1 - z_2}\,,
\end{equation}
with conformally invariant residue $1$: no coordinate, no metric,
no level. At three points, the Arnold relation
\begin{equation}\label{eq:arnold}
\eta_{12} \wedge \eta_{23}
+ \eta_{23} \wedge \eta_{31}
+ \eta_{31} \wedge \eta_{12}
\;=\; 0
\end{equation}
generates all relations in
$H^*(\Conf_n(\mathbf{C}), \mathbf{C})$. The bar
differential squares to zero if and only if the $n$-th products
satisfy the Borcherds identity; the Arnold relation kills the
differential form, the Borcherds identity kills the algebra, and
both are consumed simultaneously. This is the \emph{selection
principle}: configuration space geometry determines the algebraic
axioms; the bar construction accepts exactly chiral algebras.

The binary collision residue of the bar differential is the
classical $R$-matrix
\[
r_\cA(z) \;=\;
\Res^{\mathrm{coll}}_{0,2}(\Theta_\cA)
\;\in\; \operatorname{End}_\cA(2)[\![z^{-1}]\!],
\]
where $\Theta_\cA := D_\cA - d_0$ is the Maurer--Cartan element
of the bar differential, satisfying
$d\Theta_\cA + \tfrac{1}{2}[\Theta_\cA, \Theta_\cA] = 0$
automatically because $(D_\cA)^2 = 0$. The
$\Sigma_n$-coinvariant quotient erases the matrix structure and
retains only the scalar
\begin{equation}\label{eq:kappa-def}
\kappa(\cA) \;=\; \av(r_\cA(z))
\quad \text{for abelian and scalar families,}
\end{equation}
while for non-abelian affine Kac--Moody
\[
\kappa(V_k(\fg)) \;=\; \av(r_\cA(z)) + \dim(\fg)/2.
\]
the modular characteristic: the single number that survives
averaging. Five structural theorems extract the
$\Sigma_n$-invariant content of the ordered bar. Each theorem
characterizes one facet of $\Theta_\cA$:
\begin{enumerate}[label=\textup{(\Alph*)}]
\item \emph{Reflection}: $K^2 \simeq \mathrm{id}$ on
 $\mathrm{Kosz}(X)$ (chiral Koszul reflection at level
 $1 \leftrightarrow 2$).
\item \emph{Inversion}: $\Omega_X(\barB_X(C)) \xrightarrow{\sim} C$
 in $D^{\mathrm{co}}_{\mathrm{ch}}(X)$ (level $1 \to 3$).
\item \emph{Stratification}: the $5 \times 5$ $\kappa$-stratification
 matrix on rows $\mathsf{G/L/C/M/B}$ at level~$5$ per stratum,
 with $K3 \times E$ anchoring row $\mathsf{B}$ at
 $(0, 0, 3, 5, 24)$.
\item \emph{Leading coefficient}: $\mathrm{obs}_g = \kappa \cdot \lambda_g$
 in $H^*(\overline{\cM}_{g,n})$ (level $4$;
 $\obs_1 = \kappa \cdot \lambda_1$ unconditional;
 $\obs_g = \kappa \cdot \lambda_g$ at all genera on the
 scalar-diagonal uniform-weight lane via GRR and clutching).
\item \emph{Coefficient ring}: $\ChirHoch^\bullet \subset \{0,1,2\}$
 (level~$3$ on the Koszul locus, polynomial Hilbert series).
\end{enumerate}

The chain is forced: without~A, there is no dual at the chart
level; without~B, the bar transform can lose the chart algebra
inside the derived chiral centre; without~C, the
$\kappa$-stratification matrix collapses to a single number;
without~D, the genus tower has no distinguished scalar shadow;
without~H, the coefficient ring is uncontrolled.

The locus $\mathrm{KSDual} \subset \mathrm{Kosz}(X)$ on which
the Verdier involution $\cA \mapsto \cA^!$ acts by the identity
is the $\mathbb{Z}/2$-fixed sublocus where the four-quadrant
grid $(\text{Open} \cup \text{CY}) \times
(\text{Cat} \cup \text{Chain})$ degenerates into self-dual
form: Theorem~A is an equivalence (not adjunction with
comparison map), Theorem~H is exact in $\{0, 1, 2\}$, the
five-archetype dichotomy stabilises, and
$\kappa_{\mathrm{BKM}}(\Phi_N) = c_N(0)/2$ is the equivariant
signature for $N \in \{1, 2, 3, 4, 6\}$ plus half- and
quarter-integer continuations. Self-dual points include the
Heisenberg locus $K = 0$ and the Virasoro fixed point
$c = 13$.

\subsection{Prior work}

Five existing programmes address aspects of the problem.
Beilinson--Drinfeld \cite{BD04} construct factorization algebras on
$\Ran(X)$ and prove chiral homology is well-defined, but do not
treat bar-cobar inversion, complementarity, or the genus tower.
Francis--Gaitsgory \cite{FG12} establish chiral Koszul duality at
genus $0$ for Lie-type bar complexes; their framework does not
reach higher genera or the full tensor bar.
Costello--Gwilliam \cite{CG17} develop factorization algebras for
perturbative QFT; they do not treat Koszul duality or the modular
characteristic.
Gui--Li--Zeng \cite{GLZ24} prove a quadratic duality at the
cochain level, a genus-$0$ degree-$2$ result.
Malikov--Schechtman \cite{MS24} construct homotopy chiral algebras
as the correct input, but do not prove the five structural
theorems.

\begin{center}
\small
\begin{tabular}{l@{\quad}c@{\quad}c@{\quad}c@{\quad}c@{\quad}c}
\toprule
& \textbf{A} & \textbf{B} & \textbf{C} & \textbf{D} & \textbf{H} \\
\textbf{Programme}
& \footnotesize adjunction
& \footnotesize inversion
& \footnotesize compl.
& \footnotesize genus
& \footnotesize chiral Hochschild \\
\midrule
BD \cite{BD04}
 & $\checkmark$ & & & & \\
FG \cite{FG12}
 & $\checkmark$ & $\checkmark^*$ & & & \\
CG \cite{CG17}
 & & & & & \\
GLZ \cite{GLZ24}
 & $\checkmark^*$ & & & & \\
MS \cite{MS24}
 & & & & & \\
\textbf{This work}
 & $\checkmark$ & $\checkmark$ & $\checkmark$
 & $\checkmark$ & $\checkmark$ \\
\bottomrule
\end{tabular}
\end{center}

\noindent
{\footnotesize ${}^*$FG: genus $0$, Lie-type. GLZ: genus $0$,
degree $2$.}

\subsection{The Heisenberg computation}

The Heisenberg chiral algebra $\cH_k$ is generated by a single
current $J$ of conformal weight $1$ with OPE
$J(z)\,J(w) \sim k/(z-w)^2$. One generator, one double pole, no
simple pole. The binary residue of the bar differential is the
complete computation:
\[
d_{\barB}[s^{-1}J \,|\, s^{-1}J]
\;=\;
\Res_{z_1 = z_2}\!\left[
 \frac{k}{(z_1 - z_2)^2} \cdot d\log(z_1 - z_2)
\right]
\;=\; k.
\]
The modular characteristic is
$\kappa(\cH_k) = k$, the collision residue
$r(z) = k/z$ (scalar, not matrix), bar-cobar inversion gives
$\Omega(\barB(\cH_k)) \simeq \cH_k$, complementarity yields
$\kappa(\cH_k) + \kappa(\cH_k^!) = k + (-k) = 0$, genus
universality produces $F_1 = k/24$ and the $\Ahat$-series at all
genera for this scalar-diagonal uniform-weight algebra, and chiral
Hochschild gives
$P(t) = 1 + t + t^2$. Every clause of every theorem is verified
in a single example. Every other family is a variation on this
computation, with increasingly complex collision residues.


\subsection{Conventions}

Throughout, $X$ denotes a smooth projective curve over
$\mathbf{C}$, $\cA$ a chiral algebra on $X$ in the sense of
Beilinson--Drinfeld \cite{BD04}, and $\Mbar_g = \Mbar_{g,0}$ the
Deligne--Mumford moduli space of stable curves of genus $g$.
Grading is cohomological: $|d| = +1$. Desuspension lowers degree:
$|s^{-1}v| = |v| - 1$. The bar complex uses the augmentation ideal:
$\barB(\cA) = T^c(s^{-1}\Abar)$ with $\Abar = \ker(\varepsilon)$.
The Fulton--MacPherson compactification $\overline{\FM}_n(X)$ is the
real oriented blowup of $X^n$ along all diagonal strata; it is a
manifold with corners whose codimension-one faces $D_S$ are
indexed by subsets $S \subseteq \{1, \ldots, n\}$ with $|S| \geq 2$.


%%% ================================================================
%%% SECTION 2: THE BAR COMPLEX
%%% ================================================================

\section{The bar complex on algebraic curves}
\label{sec:bar-complex}

\subsection{Chiral algebras}

A \emph{chiral algebra} $\cA$ on a smooth curve $X$
\cite{BD04} is a $\cD_X$-module equipped with a chiral bracket
\begin{equation}\label{eq:chiral-bracket}
\mu^{\mathrm{ch}} \colon
j_* j^*(\cA \boxtimes \cA)
\longrightarrow
\Delta_!(\cA),
\end{equation}
where $j \colon X^2 \setminus \Delta \hookrightarrow X^2$ is the
complement of the diagonal and $\Delta_!$ is the $!$-pushforward
along the diagonal embedding. In local coordinates, the chiral
bracket encodes the operator product expansion:
\[
a(z)\,b(w) \;\sim\;
\sum_{n \geq 0} \frac{a_{(n)}b(w)}{(z-w)^{n+1}}.
\]
The zeroth product $a_{(0)}b$ is the Lie bracket (first-order
pole); the first product $a_{(1)}b$ carries the symmetric inner
product (second-order pole). The Borcherds identity
\begin{equation}\label{eq:borcherds}
\sum_{j \geq 0} \binom{m}{j}
(a_{(n+j)}b)_{(m+k-j)}c
\;=\;
\sum_{j \geq 0} (-1)^j \binom{n}{j}
\left(
a_{(m+n-j)}(b_{(k+j)}c)
- (-1)^n\, b_{(n+k-j)}(a_{(m+j)}c)
\right)
\end{equation}
is the defining axiom: it couples all pole orders in a single
constraint.

\subsection{The propagator and the Arnold relation}

The bar differential extracts OPE data from collisions
on $C_2(X) = X \times X \setminus \Delta$. A regular form has
residue zero and extracts nothing. A double pole transforms under
coordinate change and has no coordinate-invariant residue. A
simple pole is forced; among $1$-forms with a first-order pole
along $\Delta$, only the logarithmic derivative has conformally
invariant residue:
\[
\eta_{12} = d\log(z_1 - z_2)
= \frac{dz_1 - dz_2}{z_1 - z_2}\,,
\qquad \Res_\Delta\, \eta_{12} = 1.
\]
This is the \emph{propagator}: weight $1$, no dependence on level,
metric, or conformal structure.

Under $z \mapsto w(z)$, the propagator transforms as
$\eta_{12} \mapsto \eta_{12}
+ d\log\frac{w(z_1) - w(z_2)}{z_1 - z_2}$; near the diagonal
the correction reduces to $d\log w'(z_i)$, the standard cocycle
for $\mathrm{Diff}(X)$. This failure of invariance is not a
defect; it is the datum that the Virasoro algebra measures.

At three points, the Arnold relation
\[
\eta_{12} \wedge \eta_{23}
+ \eta_{23} \wedge \eta_{31}
+ \eta_{31} \wedge \eta_{12}
= 0
\]
restates the partial-fractions identity
\[
\frac{1}{(z_1 - z_2)(z_2 - z_3)}
+ \frac{1}{(z_2 - z_3)(z_3 - z_1)}
+ \frac{1}{(z_3 - z_1)(z_1 - z_2)}
= 0.
\]
Arnold proved that, replicated across all triples
$\{i,j,k\} \subset \{1, \ldots, n\}$, this generates the
complete ideal of relations in
$H^*(\Conf_n(\mathbf{C}), \mathbf{C})$.

\subsection{The ordered bar complex}

\begin{definition}[Ordered bar complex]\label{def:ordered-bar}
Let $\cA$ be a chiral algebra on a smooth curve $X$,
$\Abar = \ker(\varepsilon)$ the augmentation ideal.
The \emph{ordered bar complex} is
\begin{equation}\label{eq:bar-full}
\barB^{\mathrm{ord}}_X(\cA)
\;=\;
\bigoplus_{n \geq 1}
(s^{-1}\Abar)^{\otimes n}
\otimes
\Gamma\bigl(\overline{\FM}_n(X),\,
\Omega^{n-1}_{\log}\bigr),
\end{equation}
with no $\Sigma_n$-quotient. Here $s^{-1}$ denotes
desuspension ($|s^{-1}a| = |a| - 1$), and the cohomological
convention $|d| = +1$ is used throughout.
\end{definition}

The bar differential decomposes into three pieces:
\begin{equation}\label{eq:bar-diff}
d_{\barB} = d_{\mathrm{int}} + d_{\mathrm{res}} + d_{\mathrm{dR}}.
\end{equation}
The internal differential $d_{\mathrm{int}}$ acts on each tensor
factor of $\cA$. The de Rham differential $d_{\mathrm{dR}}$ acts
on logarithmic forms on $\overline{\FM}_n(X)$. The residue
differential $d_{\mathrm{res}}$ extracts OPE data at collision
divisors: for a codimension-one face $D_{\{i,j\}}$ corresponding to
the collision $z_i \to z_j$,
\begin{equation}\label{eq:res-diff}
d_{\mathrm{res}}^{(ij)}
\bigl(
a_1 \otimes \cdots \otimes a_n \otimes \eta_{ij} \wedge \omega'
\bigr)
\;=\;
\pm\,
a_1 \otimes \cdots \otimes
\widehat{a_i} \otimes \cdots \otimes
\widehat{a_j} \otimes \cdots \otimes
a_{i(p)}a_j
\otimes \omega',
\end{equation}
where $p$ is the pole order, hats denote omission, and
$a_{(p)}b$ is the $p$-th Fourier mode of the OPE.

\subsection{Why $d^2 = 0$: the Borcherds selection principle}

\begin{theorem}[Bar nilpotence]\label{thm:bar-nilpotence}
The bar differential satisfies $d_{\barB}^2 = 0$ if and only if
the $n$-th products of $\cA$ satisfy the Borcherds
identity~\eqref{eq:borcherds}.
\end{theorem}

\begin{proof}
Expand $(d_{\mathrm{int}} + d_{\mathrm{res}} + d_{\mathrm{dR}})^2$
into nine terms. Three vanish individually:
$d_{\mathrm{int}}^2 = 0$ (cochain complex),
$d_{\mathrm{dR}}^2 = 0$ (de Rham), and
$\{d_{\mathrm{int}}, d_{\mathrm{dR}}\} = 0$ (Leibniz). The
remaining terms are controlled by index overlap in the residue
operator:

\emph{Disjoint indices}
($\{i,j\} \cap \{k,\ell\} = \emptyset$): residue operators
commute; cancellation is by the Koszul sign rule. No condition on
the OPE.

\emph{One shared index} (say $j = k$): three boundary strata meet
at the codimension-$2$ locus $D_{ij\ell}$ of triple collision.
The cyclic sum of iterated residues vanishes if and only if the
Borcherds identity holds. The Arnold relation kills the
differential form; the Borcherds identity kills the algebra.
Both are consumed.

\emph{Same pair} ($\{i,j\} = \{k,\ell\}$):
$(\Res_{D_{ij}})^2 = 0$ by degree.
\end{proof}

\begin{remark}[Selection table]\label{rem:selection-table}
The bar construction asks the same question at every level
of geometry:
\begin{center}
\small
\begin{tabular}{lll}
\textbf{Base} & \textbf{Condition for $d^2 = 0$}
 & \textbf{Selected objects} \\
\hline
Point & Jacobi identity & Lie algebras \\
Curve $X$ & Borcherds identity & Chiral algebras \\
$X$ over $\Mbar_g$ & $+$ period corrections
 & Modular Koszul algebras
\end{tabular}
\end{center}
Each row is forced by the geometry of the next.
\end{remark}

\subsection{Two coproducts}

The ordered bar carries the \emph{deconcatenation
coproduct}~\eqref{eq:deconcatenation}: $n+1$ terms, coassociative
but not cocommutative, an $\Eone$-coalgebra reflecting the
linear ordering. The $\Sigma_n$-coinvariant quotient
\[
\barB^\Sigma_X(\cA)
\;=\;
\bigoplus_{n \geq 1}
(s^{-1}\Abar)^{\otimes n}_{\Sigma_n}
\otimes
\Gamma\bigl(\overline{\FM}_n(X),\,
\Omega^{n-1}_{\log}\bigr)
\]
carries the \emph{coshuffle coproduct}: $2^n$ terms,
coassociative and cocommutative, an $\Einf$-coalgebra. The
ordered bar is the level-$2$ object before symmetrisation; the symmetric bar is the lossy
projection that discards the $R$-matrix.

\subsection{From genus $0$ to all genera}

At genus $g \geq 1$, the function $z_1 - z_2$ has no global
meaning; the propagator must be replaced by
$d\log E(z_1, z_2)$, where $E(z,w)$ is the prime form on a
Riemann surface of genus $g$ (a section of
$K^{-1/2} \boxtimes K^{-1/2}$, weight $1$). The bar differential
acquires curvature:
\begin{equation}\label{eq:curvature}
(d_{\mathrm{fib}}^{\mathrm{ord}})^2
\;=\; r_\cA(z) \cdot \omega_g,
\end{equation}
matrix-valued in
$\operatorname{End}_\cA(2) \otimes H^{1,1}(\cC_g)$, where
$\omega_g = c_1(\mathbb{E})$ is the Hodge class on $\Mbar_g$.
Averaging over $\Sigma_2$ collapses this to the scalar equation
$d_{\mathrm{fib}}^2 = \kappa(\cA) \cdot \omega_g$.

The \emph{total} bar differential
$D_\cA = \sum_{g \geq 0} \hbar^g\, d_\cA^{(g)}$ absorbs the
curvature into the genus expansion: $D_\cA^2 = 0$
unconditionally.

\begin{definition}[Modular characteristic]\label{def:kappa}
The \emph{modular characteristic} \(\kappa(\cA)\) is the genus-one
scalar obstruction. In scalar or abelian cases it equals the averaged
collision residue. For nonabelian affine Kac--Moody algebras in the
trace-form normalization,
\[
\kappa(V_k(\fg))
\;=\;
\av(r^{\mathrm{coll}})+\frac{\dim(\fg)}{2}
\;=\;
\frac{\dim(\fg)(k+h^\vee)}{2h^\vee},
\]
where the second summand is the Sugawara simple-pole contribution.
\end{definition}

\begin{definition}[Maurer--Cartan element]\label{def:mc}
The \emph{Maurer--Cartan element} is
$\Theta_\cA := D_\cA - d_0 \in \gAmod$, the positive-genus
part of the bar differential. Since $D_\cA^2 = 0$, it satisfies
\begin{equation}\label{eq:mc}
d_0\, \Theta_\cA + \tfrac{1}{2}[\Theta_\cA, \Theta_\cA] = 0
\end{equation}
unconditionally. Existence of the MC element is a tautology
of the bar construction; the five theorems characterize its
structure.
\end{definition}


%%% ================================================================
%%% SECTION 3: THEOREM A
%%% ================================================================

\section{Theorem A: chiral Koszul reflection $K^2 \simeq \mathrm{id}$}
\label{sec:theorem-A}

\subsection{Statement}

The bar complex produces a coalgebra; the question is what
algebra it encodes.  Three functors act on the bar complex
and produce three distinct outputs:
\begin{equation}\label{eq:three-functors}
\begin{array}{lcll}
\Omega(\barB(\cA)) &\simeq& \cA
 & \text{(inversion: recovers the original),}\\[3pt]
\mathbb{D}_{\Ran}(\barB(\cA)) &\simeq& \cA^!_\infty
 & \text{(Verdier: the homotopy dual),}\\[3pt]
(H^*(\barB(\cA)))^\vee &=& \cA^!
 & \text{(linear duality: the strict dual).}
\end{array}
\end{equation}
Confusing any two is a category error: cobar inverts, Verdier
dualizes at chain level, and linear duality produces the strict
dual.

\begin{definition}[The homotopy Koszul dual $\cA^!_\infty$; explicit construction]
\label{def:A-bang-infty}
For an augmented chiral algebra $\cA$ on a smooth curve~$X$ over a field of characteristic zero, define the \emph{homotopy Koszul dual factorization algebra} by
\[
  \cA^!_\infty \;:=\; \mathbb{D}_{\Ran}\bigl(\barB_X(\cA)\bigr),
\]
the Verdier dual of the bar factorization coalgebra on $\Ran(X)$. Equivalently (Lowen--Positselski homotopy-coalgebra duality for conilpotent complete objects), $\cA^!_\infty$ is the chiral algebra freely generated by $s\,\Abar^\vee$ together with an $A_\infty$-structure obtained by transferring the cooperations of $\barB_X(\cA)$ through a contraction onto its cohomology, under the finiteness hypothesis that $\barB_X(\cA)$ is degreewise finite-dimensional in each bar-depth stratum (satisfied by every freely strongly generated chiral algebra, including Heisenberg, affine Kac--Moody at generic level, Virasoro, and the principal $\mathcal{W}_N$). On the Koszul locus this $A_\infty$-structure strictifies to a genuine chiral algebra structure whose cohomology is the strict Koszul dual: $H^*(\cA^!_\infty)\cong \cA^!$.
\end{definition}

\begin{theorem}[Theorem A: chiral Koszul reflection $K^2 \simeq \mathrm{id}$, parametric strength]
\label{thm:bar-cobar-adjunction}
\textsc{Type signature.} Quadrant: Open. Presentation: chain-level
$+$ $(\infty,2)$-properad. Level: $1 \leftrightarrow 2$
(chart $A_b \leftrightarrow$ bar coalgebra $\barB_X(A_b)$).
Hypothesis package: $(H1)$ augmented; $(H2)$ augmentation-ideal
complete (Positselski-weakly curved); $(H3)$ finite-dimensional
graded bar pieces in the conformal-weight grading.

Let $X$ be a smooth projective curve over a field of
characteristic~$0$, $\cA = A_b = \mathrm{End}_{\mathcal{C}}(b)$ the
chart algebra at a vacuum $b$ in the factorization dg-category
$\mathcal{C}^{\mathrm{op}}$ on $(X, D, \tau)$, with bar complex
$\barB_X(\cA)$ in the finite-bar class of Definition~\textup{\ref{def:A-bang-infty}}.
\begin{enumerate}[label=\textup{(T1\alph*)}]
\item \emph{Weak strength} \textup{(unconditional in the weight-completed ambient under $(H1)$ alone)}: the bar and cobar functors form an adjoint pair
 \[
 \barB_X \colon
 \mathrm{Alg}_{\mathrm{aug}}(\mathrm{Fact}(X))
 \rightleftarrows
 \mathrm{CoAlg}_{\mathrm{conil}}(\mathrm{Fact}(X))
 \,:\! \Omega_X
 \]
 with unit $\eta\colon \mathrm{id} \to \Omega_X\circ \barB_X$ and counit $\varepsilon\colon \barB_X\circ \Omega_X \to \mathrm{id}$, natural in $\cA$ within the Francis--Gaitsgory factorization ambient of~\cite{FG12}, provided that ambient is taken in its \emph{weight-completed} / pro-conilpotent form $\mathrm{pro}\text{-}\mathrm{CoAlg}_{\mathrm{conil}}(\mathrm{Fact}(X))$ whenever $\cA$ has unbounded conformal-weight grading (classes~$\mathsf{G}$,~$\mathsf{L}$ with positive-energy grading and, a fortiori, class~$\mathsf{M}$). On the raw bounded direct-sum ambient $\mathrm{Ch}(\mathrm{Vect})$ the target $\mathrm{CoAlg}_{\mathrm{conil}}$ is too small for class~$\mathsf{M}$: the bar coalgebra $\barB(\mathrm{Vir}_c)$ fails conilpotency because $L_0 \in \barB^1$ has $\bar{\Delta}^{(N)}(L_0) \neq 0$ for every $N \ge 1$ (Remark~\textup{\ref{rem:T1a-ambient-classM}}; same $L_0$-obstruction as Theorem~B~(B.2), \verb|thm:chiral-positselski-weight-completed|).
\item \emph{Strong strength: Verdier intertwining $\mathbb{D}_{\Ran}\, \barB_X \simeq \cA^!_\infty$} \textup{(unconditional under $(H1) + (H3)$)}: Verdier duality on $\Ran(X)$ intertwines the bar with the homotopy Koszul dual of Definition~\textup{\ref{def:A-bang-infty}}:
 \[
 \mathbb{D}_{\Ran}\, \barB_X(\cA) \;\simeq\; \cA^!_\infty.
 \]
 No Koszul hypothesis is invoked at this strength; $\cA^!_\infty$ carries $A_\infty$-structure measuring the failure of strict Koszulness.
\item \emph{Strongest strength: $K^2 \simeq \mathrm{id}$ on $\mathrm{Kosz}(X)$} \textup{(under $(H1) + (H2) + (H3)$)}: on the Koszul locus, where a twisting morphism $\tau\colon \cC \to \cA$ with $\cC$ conilpotent makes $K_\tau^L(\cA, \cC)$ acyclic (equivalently the PBW spectral sequence collapses at $E_2$), the chiral Koszul reflection
 \[
 K_X(\cA) \;:=\; \Omega_X\,\mathbb{D}_{\Ran}\,\barB_X(\cA),
 \qquad K_X^2 \simeq \mathrm{id}_{\mathrm{Kosz}(X)},
 \]
 is an involution on $\mathrm{Kosz}(X)$, the unit of \textup{(T1a)} and the intertwining of \textup{(T1b)} become quasi-isomorphisms,
 \[
 \cC \xrightarrow{\;\sim\;} \barB_X(\cA),
 \qquad
 \Omega_X(\cC) \xrightarrow{\;\sim\;} \cA,
 \qquad
 H^*(\cA^!_\infty) \cong \cA^!,
 \]
 and on the $\mathbb{Z}/2$-fixed sublocus
 $\mathrm{KSDual} \subset \mathrm{Kosz}(X)$ the reflection is the identity.
\item \emph{Strongest rejected strength}: the assertion that the adjunction of \textup{(T1a)} is an equivalence on the full $\mathrm{Alg}^{\mathrm{aug}}$ off the Koszul locus, in the raw direct-sum ambient $\mathrm{Ch}(\mathrm{Vect})$, is false. The witness is the same $L_0$-obstruction as in \textup{(T1a)}: $L_0 \in \barB^1(\mathrm{Vir}_c)$ has $\bar{\Delta}^{(N)}(L_0) \neq 0$ for every $N \ge 1$, so $\barB_X(\mathrm{Vir}_c)$ exits $\mathrm{CoAlg}_{\mathrm{conil}}$ at the raw direct-sum level. The Koszul hypothesis or the weight-completed ambient is structurally required; bundling the unconditional adjunction \textup{(T1a)} with the Koszul-locus reflection \textup{(T1c)} into a single ambient-free equivalence mistakes the forgetful image for the source.
\end{enumerate}
\end{theorem}

\begin{remark}[Four parametric strengths, disjoint inputs]\label{rem:T1-threeway}
The partition into \textup{(T1a)} weak, \textup{(T1b)} strong,
\textup{(T1c)} strongest, \textup{(T1d)} strongest-rejected
separates parametric strengths with disjoint load-bearing inputs:
weak adjunction uses only the cofree/free universal properties
and the Francis--Gaitsgory ambient~\cite{FG12} weight-completed when
the conformal-weight grading is unbounded; Verdier intertwining
uses the six-functor formalism on $\Ran(X)$ together with the
finiteness hypothesis~$(H3)$; the Koszul reflection
$K^2 \simeq \mathrm{id}$ uses Koszul acyclicity / PBW $E_2$-collapse;
the rejected strength names the boundary precisely so that no
claim accidentally crosses it. Bundling weak and strong into a
single equivalence conflates universal properties and produces
the false slogan ``$\mathrm{Bar}(A)$ is the bulk'': the
bar coalgebra is the twisting object at level~$2$, and the bulk
is $Z^{\mathrm{der}}_{\mathrm{ch}}(A)$ at level~$3$.
\end{remark}

\begin{remark}[Ambient qualifier for \textup{(T1a)}; class-$\mathsf{M}$ at the raw direct sum]\label{rem:T1a-ambient-classM}
The adjunction $\barB_X \dashv \Omega_X$ is a formal consequence of the free/cofree universal properties in the chiral factorization setting of Francis--Gaitsgory~\cite{FG12}, \emph{provided} the target coalgebra category genuinely contains $\barB_X(\cA)$. For class~$\mathsf{G}$ (Heisenberg) and class~$\mathsf{L}$ (affine Kac--Moody away from critical level) the bar coalgebra is conilpotent already at the bounded direct-sum ambient $\mathrm{Ch}(\mathrm{Vect})$, so the adjunction lands in $\mathrm{CoAlg}_{\mathrm{conil}}(\mathrm{Fact}(X))$ without further completion. For class~$\mathsf{M}$ (Virasoro, $\cW_N$, critical-level Kac--Moody) and, more generally, for any chiral algebra whose bar filtration $F^n = \bigoplus_{k\le n} B_k$ has unbounded conformal weight, conilpotency of $\barB_X(\cA)$ fails on the raw direct sum: the $L_0$-witness $\bar{\Delta}^{(N)}(L_0)\neq 0$ for every $N\ge 1$ in $\barB^1(\mathrm{Vir}_c)$ (the Vir raw bar proposition in \verb|chapters/theory/theorem_B_scope_platonic.tex|). The correct ambient is then the pro-conilpotent / weight-completed factorization category $\mathrm{pro}\text{-}\mathrm{CoAlg}_{\mathrm{conil}}(\mathrm{Fact}(X))$ against the strong filtration, in which conilpotency is restored at every finite-weight truncation and the Mittag--Leffler--Milnor passage to the inverse limit converges, exactly as in Theorem~B~(B.2), \verb|thm:chiral-positselski-weight-completed|, \verb|thm:completed-bar-cobar-strong|. In this precise sense \textup{(T1a)} and Theorem~B~(B.2) share a single ambient discipline: the unconditional statement is at the weight-completed level, and the raw direct-sum statement for class~$\mathsf{M}$ is genuinely false (not a gap) and should not be asserted at that ambient.
\end{remark}

\subsection{Proof}

\emph{Step 1: The twisting morphism.} A chiral twisting morphism
$\tau \colon \cC \to \cA$ is a degree-$+1$ element in the chiral
convolution algebra satisfying the Maurer--Cartan equation
$d\tau + \tau \star \tau = 0$, where the star product is mediated
by the integration kernel $\eta_{12}$ on
$X^2 \setminus \Delta$. The acyclicity of the twisted tensor
product $K_\tau^L(\cA, \cC)$ is the defining property of a
chiral Koszul pair.

\emph{Step 2: The PBW recognition criterion.} The PBW filtration
on $\cA$ by bar-length makes the associated graded
quadratic-Koszul in the classical sense. The chiral algebra need
not be quadratic (the Virasoro OPE has a quartic pole, $\cW$-algebras
have poles of arbitrary order); what matters is that the
leading-order structure under the PBW filtration is. The $E_2$
page of the bar spectral sequence identifies with the classical
bar complex of the associated graded, and the collapse at
$E_2$ is the chiral Koszul condition.

\emph{Step 3: Verdier intertwining.} Verdier duality
$\mathbb{D}_{\Ran}$ on $\Ran(X)$ converts coalgebras to algebras.
Applied to $\barB_X(\cA)$, it produces a factorization algebra
$\cA^!_\infty$ on $\Ran(X)$. The key identity is
\[
\mathbb{D}_{\Ran}(T^c(s^{-1}\Abar))
\;\simeq\;
T(s\, (H^*(\barB(\cA)))^\vee),
\]
where the left side is the Verdier dual of the cofree coalgebra
and the right side is the free algebra on the linear dual of
bar cohomology. On the Koszul locus, bar cohomology
concentrates in degree $1$, and the right side reduces to the
strict Koszul dual algebra $\cA^!$.

\emph{Step 4: Filtered comparison.} The filtered comparison
lemma establishes that the PBW spectral sequence is compatible
with the Verdier functor: the filtration on $\barB_X(\cA)$
induced by bar degree is taken by $\mathbb{D}_{\Ran}$ to the
dual filtration on $\cA^!_\infty$. This is the non-formal content
of the theorem; the compatibility is not automatic and requires
the Fulton--MacPherson boundary structure.

\begin{example}[Heisenberg]\label{ex:thmA-heis}
For $\cA = \cH_k$: the bar complex
$\barB(\cH_k) = T^c(s^{-1}\mathbf{C} \cdot J)$ has bar
cohomology concentrated in degree $1$
($H^{-1}(\barB(\cH_k)) = \mathbf{C} \cdot s^{-1}J$).
The Koszul dual coalgebra is
$\cH_k^{\mathrm{i}} = \mathbf{C} \cdot s^{-1}J$; the strict
Koszul dual is the curved symmetric chiral algebra
$\cH_k^! = \mathrm{Sym}^{\mathrm{ch}}(V^*)$ with curvature
$m_0 = -k\omega$. The Verdier dual recovers
$\cH_k^!$ at the level of cohomology. The complementarity sum:
$\kappa(\cH_k) + \kappa(\cH_k^!) = k + (-k) = 0$.
\end{example}


%%% ================================================================
%%% SECTION 4: THEOREM B
%%% ================================================================

\section{Theorem B: bar-cobar inversion on the Koszul locus}
\label{sec:theorem-B}

\subsection{Statement}

Theorem~A constructs the dual algebra $\cA^!_\infty$, but does
not prove that the bar transform is faithful: the coalgebra
$\barB(\cA)$ could in principle fail to reconstruct~$\cA$.

\begin{theorem}[Theorem B: bar-cobar inversion on the Koszul locus]
\label{thm:bar-cobar-inversion}
\textsc{Type signature.} Quadrant: Open. Presentation: chain-level
in $D^{\mathrm{co}}_{\mathrm{ch}}(X)$. Level: $1 \to 3$
(chart $A_b$ recovered from bar coalgebra; identity on the
Koszul locus inside the derived chiral centre via Theorem~A).
Hypothesis package: chiral Koszul (twisting morphism with
acyclic twisted tensor product, equivalently PBW $E_2$-collapse);
class-$\mathsf{M}$ chain-level requires the weight-completed /
pro / $J$-adic ambient.

Let $\cA = A_b$ be a chirally Koszul chart algebra on a smooth
curve $X$ in the Beilinson tower of the factorization dg-category
$\mathcal{C}^{\mathrm{op}}$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Genus $0$, classes $\mathsf{G}$ and $\mathsf{L}$ (unconditional in $\mathrm{Ch}(\mathrm{Vect})$).}
 The cobar-bar counit is a quasi-isomorphism:
 \[
 \varepsilon \colon
 \Omega_X(\barB_X(\cA))
 \xrightarrow{\;\sim\;}
 \cA \qquad \text{in } D^{\mathrm{co}}_{\mathrm{ch}}(X).
 \]
 The bar spectral sequence collapses at $E_2$, and bar
 cohomology concentrates in bar degree $1$:
 $H^*(\barB(\cA)) \cong (s\, \cA^{\mathrm{i}})$, identifying
 the Koszul dual coalgebra. Class $\mathsf{G}$ admits an explicit
 MacLane splitting; class $\mathsf{L}$ uses PBW $E_2$-collapse.

\item \emph{Genus $g \geq 1$ on the standard landscape (modular Koszul lane).}
 If $\cA$ satisfies diagonal Ext vanishing on the fibers of the
 universal curve over $\overline{\cM}_{g,n}$, the genus-$g$
 cobar-bar counit
 $\Omega^{(g)}(\barB^{(g)}(\cA)) \xrightarrow{\sim} \cA^{(g)}$
 is a quasi-isomorphism in the coderived category. On the
 Koszul / collapse loci of the standard landscape (Heisenberg,
 affine Kac--Moody at generic level, lattice vertex algebras), the
 statement is ordinary. Class~$\mathsf{M}$ (Virasoro, $\cW_N$) at
 generic central charge is genuinely false at the raw direct-sum
 ambient: the harmonic discrepancy $S_4 = 10/[c(5c+22)] \neq 0$
 forces bar cohomology at weight~$4$. The correct chain-level
 closure is the weight-completed coderived theorem
 $\mathrm{thm:chiral-positselski-weight-completed}$, with the
 Mittag--Leffler / Milnor passage to the inverse limit absorbing
 the discrepancy at every weight stage.
\end{enumerate}
\end{theorem}

\subsection{The genus-$0$ argument}

The genus-$0$ proof proceeds by spectral sequence. The PBW
filtration on $\cA$ by conformal weight induces a decreasing
filtration $F^p$ on $\barB_X(\cA)$ by bar degree: elements of
$F^p$ have at least $p$ tensor factors. The associated spectral
sequence has $E_1$ page equal to the classical bar complex
$B(\mathrm{gr}\, \cA)$ of the associated graded, and
converges to $H^*(\barB_X(\cA))$.

The Koszul condition is that $\mathrm{gr}\, \cA$ is quadratic
Koszul in the classical sense (Priddy \cite{Priddy70}). Then the
$E_1$ differential has cohomology concentrated on the diagonal:
$E_2^{p,q} = 0$ for $p \neq q$. The spectral sequence
collapses at $E_2$, and bar cohomology concentrates in bar
degree $1$. The counit map
$\varepsilon \colon \Omega_X(\barB_X(\cA)) \to \cA$ is then a
quasi-isomorphism by the comparison theorem for filtered
complexes.

\subsection{The higher-genus extension}

At genus $g \geq 1$, the fiberwise bar differential satisfies
$d_{\mathrm{fib}}^2 = \kappa(\cA) \cdot \omega_g \neq 0$:
the bar complex is curved, and the cobar functor cannot be
applied in the classical sense. The resolution uses the total
bar differential $D_\cA$ with $D_\cA^2 = 0$: the curvature is
absorbed into the genus expansion.

The genus-$g$ inversion requires two conditions:
\begin{enumerate}
\item \emph{Central curvature}: the curvature
 $d_{\mathrm{fib}}^2 = \kappa(\cA) \cdot \omega_g$ is a
 scalar multiple of the Hodge class, not an arbitrary
 endomorphism-valued class.
\item \emph{Diagonal Ext vanishing}: the twisted tensor product
 $K_\tau^L(\cA^{(g)}, \cC^{(g)})$ is acyclic at genus $g$.
\end{enumerate}

For the standard landscape, central curvature is automatic (the
Virasoro-type curvature is generated by the stress tensor) and
diagonal Ext vanishing follows from the PBW argument adapted to
the genus-$g$ bar complex. The exception is the $\beta\gamma$
system at integer spin, where the Ext group has an anomalous
contribution from the fermionic parity.

\begin{example}[Heisenberg]\label{ex:thmB-heis}
$\barB(\cH_k)$ has bar cohomology concentrated in bar degree $1$:
$H^{-1}(\barB(\cH_k)) = \mathbf{C} \cdot s^{-1}J$. The cobar
recovers $\cH_k$ as a graded algebra. Bar-cobar inversion is
unconditional at all genera: the curvature
$d_{\mathrm{fib}}^2 = k \cdot \omega_g$ is scalar, and the Ext
vanishing is automatic because the only OPE pole is of order $2$
(no Lie bracket, no higher obstructions).
\end{example}

\begin{remark}[Off the Koszul locus]\label{rem:off-koszul}
Off the Koszul locus, bar-cobar inversion fails: the spectral
sequence does not collapse at $E_2$, bar cohomology is not
concentrated in degree $1$, and the counit is not a
quasi-isomorphism. The failure is measured by the shadow
obstruction tower $\{S_r(\cA)\}_{r \geq 2}$: the degree-$r$
shadow class $S_r \in H^*(\Mbar_{0,r})$ is the obstruction
to extending the inversion from bar degree $r-1$ to bar degree
$r$. All standard chiral algebras in the landscape are chirally
Koszul; the shadow tower measures the \emph{complexity} of
their higher-genus behaviour, not the failure of duality itself.
\end{remark}


%%% ================================================================
%%% SECTION 5: THEOREM C
%%% ================================================================

\section{Theorem C: $5 \times 5$ $\kappa$-stratification matrix}
\label{sec:theorem-C}

\subsection{The problem}

At genus $g \geq 1$, the bar complex of $\cA$ and the bar
complex of its Koszul dual $\cA^!$ coexist on the same moduli
space $\Mbar_g$. The curvatures are related:
$d_{\mathrm{fib}}^2(\cA) = \kappa(\cA) \cdot \omega_g$ and
$d_{\mathrm{fib}}^2(\cA^!) = \kappa(\cA^!) \cdot \omega_g$.
The Verdier involution exchanges the two bar complexes. The
question is whether this exchange induces a canonical
decomposition of the ambient cohomology.

\subsection{Statement}

\begin{theorem}[Theorem C: $5 \times 5$ $\kappa$-stratification matrix and Lagrangian complementarity]
\label{thm:complementarity}
\textsc{Type signature.} Quadrant: Open (with vertical
equivalence to Vol~III at level~$5$). Presentation: scalar
shadow per stratum + ambient Lagrangian decomposition. Level:
$5$ per stratum (modular trace + clutching on the open
category, reading the family-stratum ceiling row by row).
Hypothesis package: five $\kappa$-measurements per family;
collapse pattern across rows fixes the archetype label;
$\kappa_{\mathrm{BKM}}(\Phi_N) = c_N(0)/2$ as the universal
identity; Borcherds weight, chiral conductor, and fibre Euler
characteristic are three different measurements.

Each chirally Koszul chart algebra $\cA = A_b$ in the standard
landscape carries five $\kappa$-measurements on the modular
trace and a Lagrangian decomposition of the genus-$g$ ambient
complex under the Verdier involution.

\begin{enumerate}[label=\textup{(C\arabic*)}]
\item \emph{The $5 \times 5$ stratification matrix.}
 Five archetypes
 $\mathsf{G}/\mathsf{L}/\mathsf{C}/\mathsf{M}/\mathsf{B}$
 with shadow depths
 $r_{\max} \in \{2, 3, 4, \infty, 5\}$ admit five
 $\kappa$-measurements:
 $(\kappa_{\mathrm{cat}},
 \kappa^{\mathrm{Hodge}}_{\mathrm{ch}},
 \kappa^{\mathrm{Heis}}_{\mathrm{ch}},
 \kappa_{\mathrm{BKM}},
 \kappa_{\mathrm{fiber}})$
 reading the categorical, Hodge-graded chiral, Heisenberg
 chiral, Borcherds, and CY-fibre weights respectively.
 \begin{center}
 \small
 \renewcommand{\arraystretch}{1.25}
 \begin{tabular}{l|ccccc}
 \toprule
 & $\kappa_{\mathrm{cat}}$
 & $\kappa^{\mathrm{Hodge}}_{\mathrm{ch}}$
 & $\kappa^{\mathrm{Heis}}_{\mathrm{ch}}$
 & $\kappa_{\mathrm{BKM}}$
 & $\kappa_{\mathrm{fiber}}$ \\
 \midrule
 $\mathsf{G}$ (Heisenberg, lattice $V_\Lambda$)
 & $0$ & $0$ & $\mathrm{rk}\,\Lambda$ & N/A & N/A \\
 $\mathsf{L}$ (affine $V_k(\fg)$, generic level)
 & $0$ & $0$ & $d(k+h^\vee)/(2h^\vee)$ & N/A & N/A \\
 $\mathsf{C}$ (free fields $\beta\gamma$, $bc$)
 & $0$ & $0$ & $6\lambda^2 - 6\lambda + 1$ & N/A & N/A \\
 $\mathsf{M}$ (Virasoro, $\cW_N$, generic $c$)
 & $0$ & $c/2$ & N/A & N/A & N/A \\
 $\mathsf{B}$ ($K3 \times E$ with $\Delta_5$)
 & $0$ & $0$ & $3$ & $5$ & $24$ \\
 \bottomrule
 \end{tabular}
 \end{center}
 The K3$\times E$ row anchors archetype $\mathsf{B}$ at
 $(0,\,0,\,3,\,5,\,24)$ with $\Delta_5$ as primitive Borcherds
 denominator and Mukai conductor
 $K^\kappa_{\mathcal B} = 2c_+(\mathrm{Mukai}(K3)) = 8$. The
 collapse pattern across rows --- which entries are nonzero,
 which are forced to vanish or to remain undefined --- is the
classification axis: five $\kappa$ are not one invariant.

\item \emph{Lagrangian eigenspace decomposition
 (proved for $g \geq 1$, ordinary on $\mathsf{G}/\mathsf{L}$,
 weight-completed on $\mathsf{M}/\mathsf{B}$).}
 For every $g \geq 0$, the genus-$g$ ambient complex
 $\mathbf{C}_g(\cA) := R\Gamma(\Mbar_g, \cZ_\cA)$
 admits a homotopy decomposition
 \begin{equation}\label{eq:lagrangian}
 \mathbf{C}_g(\cA)
 \;\simeq\;
 \mathbf{Q}_g(\cA)
 \;\oplus\;
 \mathbf{Q}_g(\cA^!),
 \end{equation}
 where $\mathbf{Q}_g(\cA)$ and $\mathbf{Q}_g(\cA^!)$ are
 Lagrangian summands with respect to the Verdier pairing of
 degree $-(3g - 3)$. At the cohomological level for
 $g \geq 1$,
 \begin{equation}\label{eq:complementarity-cohom}
 Q_g(\cA) \oplus Q_g(\cA^!)
 \;\cong\;
 H^*(\Mbar_g, \cZ_\cA),
 \end{equation}
 the two summands are eigenspaces of the Verdier involution,
 and the decomposition is canonical. At $g = 0$ the involution
 is trivial, $Q_0(\cA^!) = 0$, and no Verdier pairing of
 negative degree is invoked.

\item \emph{Family-stratum scalar ceiling
 $\kappa(\cA) + \kappa(\cA^!) = K(\cA)$.}
 The Lagrangian decomposition forces the scalar
 complementarity sum $K(\cA) = \kappa(\cA) + \kappa(\cA^!)$
 family-dependently:
 $0$ for Heisenberg, lattice, and affine Kac--Moody (sign
 reversal under Feigin--Frenkel involution
 $k \mapsto -k - 2h^\vee$);
 $13$ for Virasoro ($c \mapsto 26 - c$, self-dual at
 $c = 13$); $250/3$ for $\cW_3$;
 $98/3$ for Bershadsky--Polyakov in the principal-value
 sense across the critical pole at $k = -3$.
 The universal form is
 $\kappa + \kappa^! = \varrho_\cA \cdot K$ with
 $\varrho_{\mathrm{KM}} = \varrho_{\mathrm{free}} = 0$,
 $\varrho_{\mathrm{Vir}} = 1/2$,
 $\varrho_{\cW_N} = H_N - 1$,
 $\varrho_{\mathrm{BP}} = 1/6$.

\item \emph{Shifted-symplectic upgrade (conditional, on the
 Verdier-perfect locus).}
 If the bar-cobar normal complex is perfect and nondegenerate,
 the ambient complex carries a $(2 - d)$-shifted symplectic
 structure (PTVV), and each Lagrangian summand carries a
 shifted Lagrangian structure. The upgrade is conditional on
 perfectness and nondegeneracy; class~$\mathsf{M}$
 boundary-stratum perfectness is the open conjecture.
\end{enumerate}
\end{theorem}

\subsection{The Koszul complementarity sum}

The Lagrangian decomposition constrains the modular
characteristics of $\cA$ and $\cA^!$:
\[
\kappa(\cA) + \kappa(\cA^!) \;=\; K(\cA),
\]
where $K(\cA)$ is the \emph{Koszul complementarity conductor},
a family-dependent constant. This is not a universal zero.

\begin{proposition}[Complementarity sums]
\label{prop:complementarity-sums}
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Heisenberg:}
 $\kappa(\cH_k) = k$,\;
 $\kappa(\cH_k^!) = -k$,\;
 $K = 0$.

\item \emph{Affine Kac--Moody:}
 $\kappa(V_k(\fg)) = \frac{\dim(\fg)(k + h^\vee)}{2h^\vee}$,\;
 $\kappa(V_k(\fg)^!) = -\frac{\dim(\fg)(k + h^\vee)}{2h^\vee}$,\;
 $K = 0$.

\item \emph{Virasoro:}
 $\kappa(\mathrm{Vir}_c) = c/2$,\;
 $\kappa(\mathrm{Vir}_{26-c}) = (26-c)/2$,\;
 $K = 13$.\; Self-dual at $c = 13$.

\item \emph{Principal $\cW_N$:}
 $\kappa(\cW_N) = c \cdot (H_N - 1)$
 where $H_N = \sum_{j=1}^{N} 1/j$.\;
 $K$ is nonzero and $N$-dependent.

\item \emph{Free fields} (lattice, $\beta\gamma$, $bc$):
 $K = 0$.
\end{enumerate}
\end{proposition}

\begin{proof}
The Lagrangian decomposition of Theorem~C forces
$\kappa + \kappa^! = \varrho_\cA \cdot K$ at the level of the
scalar shadow, with $\varrho_\cA$ family-specific
($\varrho_{\mathrm{KM}} = \varrho_{\mathrm{free}} = 0$,
$\varrho_{\mathrm{Vir}} = 1/2$, $\varrho_{\cW_N} = H_N - 1$,
$\varrho_{\mathrm{BP}} = 1/6$).
For Heisenberg and affine Kac--Moody, the Koszul dual has
opposite modular characteristic (the Verdier involution
reverses the sign of $\kappa$), giving $K = 0$.
For the Virasoro algebra, $c \mapsto 26 - c$ under Koszul
duality (the ghost central charge), and
$K = c/2 + (26-c)/2 = 13$, constant. The self-dual point
$c = 13$ is the unique value where
$\kappa = \kappa' = 13/2$: the Lagrangian decomposition
is symmetric.
\end{proof}

\begin{remark}[Five objects]\label{rem:five-objects}
% FOUR OBJECTS:
% 1. B(A) = bar coalgebra = T^c(s^{-1} A-bar) with deconcatenation
% 2. A^i = H^*(B(A)) = dual coalgebra (bar cohomology)
% 3. A^! = ((A^i)^v) = dual ALGEBRA (linear dual)
% 4. Z^der_ch(A) = derived chiral center = Hochschild cochains
The five objects appearing in the complementarity theorem:
$\cA$ (the algebra), $\barB(\cA)$ (the bar coalgebra),
$\cA^{\mathrm{i}} = H^*(\barB(\cA))$ (the dual coalgebra),
$\cA^! = (\cA^{\mathrm{i}})^\vee$ (the dual algebra), and
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)
= R\Hom_{\cA \otimes \cA^{\mathrm{op}}}(\cA, \cA)$
(the derived chiral center). These are distinct objects produced by
distinct functors; conflation of any two is a category error.
\end{remark}


%%% ================================================================
%%% SECTION 6: THEOREM D
%%% ================================================================

\section{Theorem D: the genus expansion}
\label{sec:theorem-D}

\subsection{Statement}

Complementarity supplies an ambient polarization of the genus tower,
but the scalar projection $\kappa$ is already bar-intrinsic and must
still be identified genus by genus.

\begin{theorem}[Theorem D: genus universality $\mathrm{obs}_g = \kappa \cdot \lambda_g$]
\label{thm:genus-universality}
\textsc{Type signature.} Quadrant: Open. Presentation:
chain-level on the universal curve $\overline{\cC}_g \to \overline{\cM}_{g,n}$.
Level: $4$ (line / brane operators on $\overline{\cM}_{g,n}$,
realising the scalar-projection class). Hypothesis package:
chiral Koszul; scalar-diagonal uniform-weight at part~(ii);
$H^*(\overline{\cM}_{g,n})$ as the receiving cohomology with
$\lambda_g = c_g(\mathbb{E})$ the top Chern class of the Hodge
bundle.

Let $\cA = A_b$ be a chirally Koszul chart algebra with modular
characteristic $\kappa(\cA)$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Genus $1$ (unconditional).}
 The genus-$1$ obstruction class is
 \[
 \obs_1(\cA) = \kappa(\cA) \cdot \lambda_1
 \in H^*(\Mbar_{1,1}),
 \]
 and the genus-$1$ free energy is
 $F_1(\cA) = \kappa(\cA)/24$.
 The class is forced by one-dimensionality of
 $H^2(\Mbar_{1,1}) = \mathbb{Q} \cdot \lambda_1$ together with
 the bar-curvature equation $d^2_{\mathrm{fib}} = \kappa \cdot \omega_1$.

\item \emph{All genera, scalar-diagonal uniform-weight lane.}
 If the strong generators of $\cA$ have a single conformal
 weight and the scalar channel is diagonal, the obstruction
 class at every genus is
 \[
 \obs_g(\cA) = \kappa(\cA) \cdot \lambda_g
 \quad (g \geq 1),
 \]
 and the free energies are
 $F_g(\cA) = \kappa(\cA) \cdot \Ahat_g$,
 where $\Ahat_g$ is the $g$-th coefficient of the $\Ahat$-genus:
 \begin{equation}\label{eq:ahat-generating}
 \sum_{g \geq 1} F_g(\cA) \cdot \hbar^{2g}
 \;=\;
 \kappa(\cA) \cdot
 \bigl(\Ahat(i\hbar) - 1\bigr).
 \end{equation}
 Two independent proof routes converge: Grothendieck--Riemann--Roch
 on the universal curve identifies the bar curvature with the
 Hodge bundle curvature via Arakelov--Faltings (Proof~A);
 clutching propagation from the genus-$1$ base case combined with
 tautological-line support criterion (Proof~B). Each proof
 invokes disjoint external machinery; agreement is the
 consistency check.

\item \emph{Multi-weight correction with cross-channel term.}
 For multi-weight algebras at genus $g \geq 2$, the diagonal
 term remains universal but the full free energy carries a
 cross-channel correction:
 \[
 F_g(\cA) = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}
 + \delta F_g^{\mathrm{cross}}(\cA),
 \]
 with $\delta F_g^{\mathrm{cross}}$ the explicit correction
 from mixed conformal-weight interactions; vanishing for
 uniform-weight families and at $g = 1$ for all families.
 The closed form for $\delta F_g^{\mathrm{cross}}$ at general
 multi-weight $\cA$ and $g \geq 2$ is the open frontier
 ($\mathrm{F2}$).
\end{enumerate}
\end{theorem}

\begin{remark}[Scope of the all-genera statement]
\label{rem:thmD-scope}
Part~(i) is unconditional: the genus-$1$ formula
$\obs_1 = \kappa \cdot \lambda_1$ holds for every chirally
Koszul algebra, with no uniform-weight hypothesis and no
clutching input.
Part~(ii) extends the scalar factorization from genus~$1$
to all genera by propagation along the clutching morphisms
on $\partial\Mbar_g$.
The non-trivial step is \emph{clutching-uniqueness}: the
assertion that the scalar factorization propagated through
clutching agrees, at each genus, with the direct bar-complex
computation.
This step uses the bar-intrinsic scalar trace of
$\Theta_\cA$ together with the boundary structure of
$\Mbar_g$; it is proved on the uniform-weight lane where
the graph-sum formula factors through $\kappa$ alone.
An independent derivation via the Grothendieck--Riemann--Roch
theorem on the universal curve
(\S\ref{subsec:thmD-proof}) provides a second path that
bypasses clutching-uniqueness entirely.
The genus-$1$ result and the two proof paths (clutching and
GRR) are the principal structural elements; the all-genera
statement on the uniform-weight lane rests on either one.
\end{remark}

\subsection{The $\Ahat$-genus and Bernoulli numbers}

The $\Ahat$-genus has the explicit expansion
\[
\Ahat(x) - 1
\;=\;
\frac{x/2}{\sin(x/2)} - 1
\;=\;
\frac{1}{24}\,x^2
+ \frac{7}{5760}\,x^4
+ \frac{31}{967680}\,x^6
+ \cdots
\]
The coefficients are
$\Ahat_g = \frac{2^{2g-1}-1}{2^{2g-1}} \cdot
\frac{|B_{2g}|}{(2g)!}$,
where $B_{2g}$ is the $2g$-th Bernoulli number.
The leading term $\Ahat_1 = 1/24$ is universal: for every family,
$F_1 = \kappa/24$.

\subsection{The shadow obstruction tower}

The Maurer--Cartan element $\Theta_\cA$ projects at each degree
$r \geq 2$ to a shadow invariant $S_r(\cA)$; the tower
$\{S_r\}_{r \geq 2}$ classifies chiral algebras into four
complexity classes:

\begin{center}
\small
\begin{tabular}{lcccl}
\toprule
\textbf{Class} & \textbf{Depth} & $\Delta$
 & \textbf{Example} & \textbf{Behaviour} \\
\midrule
$\mathsf{G}$ (Gaussian) & $2$ & $0$ ($S_4 = 0$)
 & Heisenberg & Formal, free \\
$\mathsf{L}$ (Lie) & $3$ & $0$ ($\kappa = 0$)
 & Aff.\ KM (crit.) & Single Massey \\
$\mathsf{C}$ (Contact) & $4$ & special
 & $\beta\gamma$ & Contact then rigid \\
$\mathsf{M}$ (Mixed) & $\infty$ & $\neq 0$
 & Virasoro, $\cW_N$ & Non-formal \\
\bottomrule
\end{tabular}
\end{center}

\noindent
The critical discriminant $\Delta = 8\kappa S_4$ governs a
dichotomy: $\Delta = 0$ terminates the tower, $\Delta \neq 0$
makes it infinite. The \emph{shadow depth} $r_{\max}$
(the highest degree at which $S_r \neq 0$) takes values
$\{2, 3, 4, \infty\}$; the \emph{algebraic depth}
$d_{\mathrm{alg}} \in \{0, 1, 2, \infty\}$ measures the
internal complexity of the MC equation and admits no value $3$
or any finite value $\geq 3$: there is a gap.

\subsection{Proof architecture}
\label{subsec:thmD-proof}

The proof of genus universality proceeds in three steps.

\emph{Step 1: Genus $1$ (unconditional).} On $\Mbar_{1,1}$,
the self-loop graph $\Gamma_{\mathrm{irr}}$ contributes
$d_{\mathrm{fib}}^2 = \kappa(\cA) \cdot \omega_1$, and
integration over $\Mbar_{1,1}$ gives $F_1 = \kappa/24$.
The only invariant that contributes at genus $1$ is $\kappa$
itself (degree $2$ of the MC element); all higher shadow
coefficients $S_r$ with $r \geq 3$ are invisible at genus $1$.

\emph{Uniform-weight factorization.} For uniform-weight
algebras, the scalar obstruction class at every genus equals
$\kappa(\cA) \cdot \lambda_g$
(Proposition~\ref{prop:scalar-obs-hodge-euler}). Two verification
routes are given there: (A)~via
Grothendieck--Riemann--Roch on the universal curve, identifying
the bar curvature with the Hodge bundle curvature through the
Arakelov--Faltings theorem; (B)~via clutching propagation from
genus~$1$, using the Whitney sum formula and the injectivity
of the trace on the one-dimensional tautological line.

\emph{Multi-weight correction.} When generators have
distinct conformal weights, cross-channel propagators produce
mixed terms that do not factor through $\kappa$ alone. The
correction $\delta F_g^{\mathrm{cross}}$ is explicit and
computable from the full $R$-matrix data of the ordered bar.

\begin{remark}[Genus-$1$ anchor]\label{rem:genus-1-anchor}
The genus-$1$ formula $\obs_1 = \kappa \cdot \lambda_1$
holds for every chirally Koszul algebra, with no
uniform-weight hypothesis and no clutching input.
The genus-$1$ result of Theorem~D(i) is independent
of the all-genera mechanism.
\end{remark}

The passage from genus~$1$ to all genera is the content of
the following proposition, which closes the all-genera extension
by two independent routes.

\begin{proposition}[Scalar obstruction equals Hodge Euler class]
\label{prop:scalar-obs-hodge-euler}
Let $\cA$ be a chirally Koszul chiral algebra on the Koszul
locus whose strong generators all have the same conformal
weight and whose scalar channel is diagonal.
Let $\pi \colon \overline{\cC}_g \to \Mbar_g$ be the
universal curve, $\mathbb{E} = R^0\pi_*\omega_\pi$ the
Hodge bundle of rank~$g$, and
$\lambda_g = c_g(\mathbb{E})$ its top Chern class.
Then for all $g \geq 1$:
\begin{equation}\label{eq:scalar-obs-hodge}
\obs_g(\cA)
\;=\;
\kappa(\cA) \cdot \lambda_g
 \qquad \textup{for scalar-diagonal uniform-weight algebras}.
\end{equation}
\end{proposition}

\begin{proof}
Two independent proofs are given. Each uses the genus-$1$
identification $\obs_1 = \kappa \cdot \lambda_1$ as base case
and extends to all genera by a different mechanism.

\medskip\noindent
\begin{lemma}[Uniform-weight scalar factorization of the bar complex;
shared input to Proofs~A and~B]\label{lem:T4-shared-input}
On the uniform-weight lane, the bar complex of a modular Koszul
chiral algebra $\cA$ over a fixed smooth projective curve $\Sigma_g$
factorizes as an external tensor product
\[
  \barB(\cA)\big|_{\Sigma_g}
  \;\simeq\;
  \barB^{\mathrm{scalar}}(\cA)
  \otimes_{\mathbb Q}
  \Omega^\bullet_{\Sigma_g}(\log D)\big|_{\mathrm{unif\text{-}wt}},
\]
with $\barB^{\mathrm{scalar}}(\cA)$ a one-dimensional algebraic
factor carrying the curvature scalar $\kappa(\cA)$ (the modular
characteristic), and $\Omega^\bullet_{\Sigma_g}(\log D)$ the
logarithmic de~Rham complex with log-poles on the collision
divisor $D \subset \Sigma_g^{\times n}$. As the curve varies
over $\Mbar_g$, the zero-mode sector of the geometric factor
is the direct image $R^0\pi_*\omega_\pi = \mathbb E$ (the Hodge
bundle), and the scalar virtual class in $K^0(\Mbar_g) \otimes \mathbb Q$
is
\[
  [\barB^{(g)}_{\mathrm{scalar}}(\cA)]^{\mathrm{vir}}
  \;=\;
  \kappa(\cA)\cdot\lambda_{-1}(\mathbb E).
\]
The obstruction class is the degree-$g$ component of its Chern
character:
\[
  \obs_g(\cA)=\kappa(\cA)\,c_g(\mathbb E)
  =\kappa(\cA)\lambda_g.
\]
\end{lemma}

\begin{proof}
The uniform-weight hypothesis forces every generator of $\cA$
to have the same conformal weight, so every OPE propagator
reduces to a scalar multiple of the single weight-$1$ form
$d\log E(z,w)$ (the prime form differential). The bar differential
is therefore a tensor of an algebraic piece (scalar channel,
recording the Casimir coefficient) with a purely geometric
piece (log-de-Rham). The zero-mode reduction from the full
$\Omega^\bullet_{\Sigma_g}$ to $R^0\pi_*\omega_\pi = \mathbb E$
is the standard Hodge-theoretic restriction at the constant
term. The virtual class equation then follows because the
scalar channel contributes the constant $\kappa(\cA)$ while
the geometric channel contributes $\lambda_{-1}(\mathbb E)$. By the
splitting principle,
$\mathrm{ch}_g(\lambda_{-1}(\mathbb E))=c_g(\mathbb E)$ after the
standard obstruction-orientation convention.
\end{proof}

\begin{remark}[Two proofs, one input]\label{rem:T4-shared-input}
Lemma~\ref{lem:T4-shared-input} is the common load-bearing input
to the two proofs of Theorem~T4 that follow. Proof~A derives
$\obs_g(\cA) = \kappa(\cA)\cdot\lambda_g$ from this input by
Grothendieck--Riemann--Roch plus the Arakelov--Faltings
identification of the Hodge curvature. Proof~B derives it
from the same input by clutching propagation from the
unconditional genus-$1$ base case. The two proofs are
independent post-input: they invoke disjoint external
machinery (GRR/Arakelov vs.\ Getzler--Kapranov modular operad),
and any error in one is detected by the other. The two proofs
therefore provide \emph{redundant verification} of the same
numerical identity, not \emph{independent derivations} of its
structural origin --- the latter is furnished uniquely by
Lemma~\ref{lem:T4-shared-input}.
\end{remark}

\medskip\noindent
\textbf{Proof A: Grothendieck--Riemann--Roch on the
universal curve.}
This proof identifies the bar-complex obstruction with a
characteristic class of the Hodge bundle directly, without
induction on the genus. It takes Lemma~\ref{lem:T4-shared-input}
as input.

\emph{Virtual class on moduli.}
On the uniform-weight lane, the bar complex over a fixed
curve~$\Sigma_g$ has a one-dimensional algebraic factor
(the scalar channel) tensored with a geometric factor given by
the de~Rham complex of~$\Sigma_g$ with coefficients in
$\omega_{\Sigma_g}$, because every propagator is the standard
weight-$1$ form $d\!\log E(z,w)$.
As the curve varies over~$\Mbar_g$, the zero-mode sector of
this geometric factor is the direct image
$R^0\pi_*\omega_\pi = \mathbb{E}$.
The scalar virtual class is therefore
\[
[\barB^{(g)}_{\mathrm{scalar}}(\cA)]^{\mathrm{vir}}
\;=\;
\kappa(\cA) \cdot \lambda_{-1}(\mathbb{E})
\quad
\text{in } K^0(\Mbar_g) \otimes \mathbb{Q}.
\]

\emph{Mumford's GRR computation.}
Grothendieck--Riemann--Roch on the universal curve gives
\[
\operatorname{ch}(R\pi_*\omega_\pi)
\;=\;
\pi_*\!\bigl(\operatorname{ch}(\omega_\pi) \cdot
\operatorname{Td}(T_\pi)\bigr).
\]
The degree-$g$ component of the Chern character of the
rank-$g$ bundle $\mathbb{E}$, combined with the Newton
identities relating Chern characters to Chern classes, gives
\[
c_g(\mathbb{E}) \;=\; \lambda_g
\quad \in \operatorname{CH}^g(\Mbar_g).
\]
This is Mumford's computation~\cite{Mumford83}.

\emph{Chern--Weil identification.}
The Hodge bundle carries the Arakelov metric, whose
restriction to each fiber $H^0(\Sigma_g, \Omega^1)$ is the
$L^2$ inner product.
The Arakelov--Faltings theorem~\cite{Faltings84} identifies
the curvature of $(\mathbb{E}, h_{\mathrm{Ar}})$ with the
Arakelov $(1,1)$-form:
\[
\Theta_{\mathbb{E}}\big|_{\mathrm{fiber}}
\;=\;
\omega_g^{\mathrm{Ar}}
\;=\;
\frac{i}{2}\sum_{\alpha,\beta=1}^{g}
(\operatorname{Im}\Omega)^{-1}_{\alpha\beta}\,
\omega_\alpha \wedge \overline{\omega}_\beta.
\]
The quantum Arnold relations give the fiberwise bar curvature
$d_{\mathrm{fib}}^2 = \kappa(\cA) \cdot
\omega_g^{\mathrm{Ar}} \cdot \mathrm{id}$.
The Arakelov--Faltings theorem identifies
$\omega_g^{\mathrm{Ar}}$ with the curvature of the Hodge
bundle. Chern--Weil then yields
\[
\obs_g(\cA)
\;=\;
\operatorname{ch}_g\!\bigl(\kappa(\cA)\lambda_{-1}(\mathbb E)\bigr)
\;=\;
\kappa(\cA)\,c_g(\mathbb{E})
\;=\;
\kappa(\cA) \cdot \lambda_g.
\]
No clutching argument is used. The only external inputs are
Mumford's GRR computation of the Chern classes of~$\mathbb{E}$
and the Arakelov--Faltings identification of the Hodge
curvature.

\medskip\noindent
\textbf{Proof B: clutching propagation from genus~$1$.}
This proof uses the boundary stratification
of~$\Mbar_g$ and proceeds by induction on~$g$.

\emph{Base case.}
$\obs_1 = \kappa \cdot \lambda_1$ is proved unconditionally
(the genus-$1$ tautological group
$H^2(\Mbar_{1,1}) \cong \mathbb{Q} \cdot
\lambda_1$ is one-dimensional).

\emph{Inductive step.}
Assume $\obs_h = \kappa \cdot \lambda_h$ for all $h < g$.
The Maurer--Cartan element
$\Theta_\cA \in \mathrm{MC}(\mathrm{Def}_{\mathrm{cyc}}(\cA)
\,\widehat{\otimes}\, \mathfrak{G}^{\mathrm{mod}})$
automatically satisfies the clutching factorization by the
Getzler--Kapranov correspondence~\cite[Theorem~5.4]{GetzlerKapranov98}:
the MC equation on the Feynman transform encodes exactly the
clutching compatibility conditions.

The separating clutching
$\xi_{\mathrm{sep}} \colon
\Mbar_{g_1,1} \times \Mbar_{g_2,1} \to \Mbar_g$
(with $g_1 + g_2 = g$) gives
\[
\xi_{\mathrm{sep}}^*(\obs_g)
\;=\;
\kappa \cdot
\xi_{\mathrm{sep}}^*(\lambda_g),
\]
because the scalar channel is one-dimensional and the clutching
propagator is normalized before multiplication by the scalar curvature
\(\kappa\). The equality uses the Whitney sum formula
$\xi_{\mathrm{sep}}^*(\lambda_g)
= \sum_{i+j=g} \lambda_i \otimes \lambda_j$
for the Hodge bundle.

The non-separating clutching
$\xi_{\mathrm{nsep}} \colon \Mbar_{g-1,2} \to \Mbar_g$
gives
\[
\xi_{\mathrm{nsep}}^*(\obs_g)
\;=\;
\kappa \cdot
\xi_{\mathrm{nsep}}^*(\lambda_g),
\]
by the inductive hypothesis applied to the genus-$(g-1)$
data at the self-node vertex.

The trace functional (integration over $\Mbar_g$) satisfies
$\int_{\Mbar_g} \obs_g = F_g = \kappa \cdot \Ahat_g$
(from the bar-complex graph sum on the uniform-weight lane),
and $\int_{\Mbar_g} \lambda_g = \Ahat_g$
(the Faber--Pandharipande evaluation). Hence
\[
\ell_g(\obs_g) \;=\; \kappa \cdot \ell_g(\lambda_g).
\]

It remains to show that the joint map
$J_g = (\ell_g, \mathrm{clut}_g) \colon W_g \to
\mathbb{C} \oplus B_g$
is injective on the relevant subspace
$U_g \ni \obs_g, \lambda_g$.
On the uniform-weight lane, $U_g$ is the one-dimensional
tautological line $\mathbb{Q} \cdot \lambda_g$ (the scalar
channel produces only classes built from the Hodge bundle;
no higher Hodge bundles $R^0\pi_*\omega_\pi^{\otimes h}$
with $h \neq 1$ enter). On this one-dimensional space, the
trace $\ell_g$ is already injective (since
$\ell_g(\lambda_g) = \Ahat_g \neq 0$), so
$J_g$ is injective a fortiori.

By the tautological-line support criterion, the injectivity
of~$J_g$ together with the clutching and trace compatibilities
gives $\obs_g = \kappa \cdot \lambda_g$.

\medskip\noindent
\textbf{Agreement of the two proofs.}
Proof~A produces the identification directly from the Hodge
bundle structure on the universal curve. Proof~B produces it
inductively from the boundary stratification. The two proofs
have no logical dependency on each other: Proof~A uses GRR
and Arakelov--Faltings; Proof~B uses Getzler--Kapranov and
the tautological-line support criterion. Their agreement is a
consistency check on the framework.
\end{proof}

\begin{remark}[Resolution of the clutching-uniqueness gap]
\label{rem:clutching-gap-resolved}
The all-genera extension of Theorem~D depends on clutching
compatibility together with support on the scalar tautological line.
Proof~B above establishes this support by showing that the relevant
subspace
$U_g$ is one-dimensional on the uniform-weight lane (the
scalar channel sees only the Hodge bundle), so injectivity of
the joint map is automatic. Proof~A bypasses the question
entirely. The all-genera statement of Theorem~D(ii) is
proved on the scalar-diagonal uniform-weight lane by either route.
\end{remark}

\begin{example}[Heisenberg at all genera]\label{ex:thmD-heis}
$\kappa(\cH_k) = k$ for the scalar-diagonal single generator of
conformal weight $1$). The generating function:
\[
\sum_{g \geq 1} F_g(\cH_k) \cdot \hbar^{2g}
\;=\;
k \cdot \left(\frac{\hbar/2}{\sin(\hbar/2)} - 1\right)
\;=\;
\frac{k}{24}\,\hbar^2
+ \frac{7k}{5760}\,\hbar^4
+ \frac{31k}{967680}\,\hbar^6
+ \cdots
\]
% C24 check: F_1 = k/24, consistent with kappa/24
The chiral partition function
$Z_{\mathrm{ch}}(\cH_k) = 1/\eta(\tau)$
(where $\eta(\tau) = q^{1/24}\prod_{n \geq 1}(1 - q^n)$)
gives $F_1 = k/24$, consistent with the universal formula.
\end{example}


%%% ================================================================
%%% SECTION 7: THEOREM H
%%% ================================================================

\section{Theorem H: chiral Hochschild cohomology}
\label{sec:theorem-H}

\subsection{Statement}

Theorem~D identifies a universal genus expansion governed by
$\kappa$; the question is what constrains the coefficient ring
in which $\kappa$ lives.

\begin{theorem}[Theorem H: $\ChirHoch^\bullet \subset \{0, 1, 2\}$ on the Koszul locus]
\label{thm:hochschild}
\textsc{Type signature.} Quadrant: Open. Presentation:
chain-level $\mathrm{ChirHoch}^\bullet(A_b) =
H^\bullet(\mathrm{CoDer}(\barB(A_b)))$. Level: $3$
(derived chiral centre $Z^{\mathrm{der}}_{\mathrm{ch}}(A_b)$,
the bulk in the Beilinson tower). Hypothesis package:
finiteness (PBW Koszulity criterion + finite-type strong
generation) + completion (class~$\mathsf{M}$ chain-level
requires the completed / pro / $J$-adic ambient).

Let $\cA = A_b$ lie in the standard PBW chiral Koszul locus
with finite-type / perfectness and the required completed
Hochschild model, away from critical and non-generic loci. The
chiral Hochschild cohomology is concentrated in degrees
$\{0, 1, 2\}$:
\[
\ChirHoch^n(\cA) = 0
\quad \text{for } n \notin \{0, 1, 2\},
\]
and the Hilbert polynomial is
\begin{equation}\label{eq:hilbert-poly}
P_\cA(t)
\;=\;
\dim Z(\cA)
+ \dim \ChirHoch^1(\cA) \cdot t
+ \dim Z(\cA^!) \cdot t^2.
\end{equation}
The Verdier intertwining of Theorem~A pairs degree~$0$ with
degree~$2$, identifying $Z(\cA^!) = \mathrm{Hom}(Z(\cA), k)$ on
the Koszul locus. The Feigin--Frenkel companion at $k = -h^\vee$
(critical level) is outside the regime: the centre is
infinite-dimensional, and the $\{0, 1, 2\}$ concentration fails
in any ambient.
\end{theorem}

\begin{remark}[Three Hochschild theories: chiral, topological, categorical]
\label{warn:three-hochschild}
Three inequivalent Hochschild cohomology theories coexist: chiral,
topological, and categorical.
\emph{Chiral Hochschild}
$\ChirHoch^*(\cA) = H^*(\mathrm{CoDer}(\barB(\cA)))$ is the
cohomology of coderivations of the bar coalgebra; it lives on
the curve $X$ and has amplitude $[0,2]$ on the Koszul locus
(Theorem~H). \emph{Topological Hochschild}
$\mathrm{HH}^*_{\mathrm{top}}$ is factorization homology on
$S^1$; it lives in one dimension higher. \emph{Categorical Hochschild}
$\mathrm{HH}^*(\mathrm{Rep}(\cA))$ governs the
Drinfeld center and the $E_2$ structure. Conflating any two
produces errors.
\end{remark}

\subsection{Family-specific specializations}

\begin{proposition}[Hilbert series for standard families]
\label{prop:hilbert-families}
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Heisenberg $\cH_k$:}\;
 $P(t) = 1 + t + t^2$.\;
 Centre = $\mathbf{C}$, outer derivation $D(J) = \mathbf{1}$,
 level deformation in degree $2$.

\item \emph{Affine Kac--Moody $V_k(\fg)$ (generic level):}\;
 $\ChirHoch^1(V_k(\fg)) \cong \fg$, giving total
 dimension $\dim(\fg) + 2$.\;
 $P(t) = 1 + \dim(\fg) \cdot t + t^2$.

\item \emph{Virasoro $\mathrm{Vir}_c$ (generic):}\;
 $P(t) = 1 + t^2$.\; $\ChirHoch^1 = 0$ (no outer
 chiral derivations).

\item \emph{Principal $\cW_N$ (generic):}\;
 $P(t) = 1 + t^2$.

\item \emph{Critical level $k = -h^\vee$:}\; Outside the
 regime of Theorem~H. The Feigin--Frenkel center makes the
 cohomology unbounded.
\end{enumerate}
\end{proposition}

\subsection{Proof architecture}

The concentration proof factors through the PBW Koszulity criterion
and the completed chiral Hochschild model. Bar concentration and
Fulton--MacPherson tower collapse are parallel consequences of PBW
collapse. The identification of the Hilbert polynomial with the
dimensions of the centre and its dual follows from the Verdier
intertwining pairing degree \(0\) with degree \(2\).

The configuration-space collapse uses Fulton--MacPherson
formality: the spectral sequence from the FM filtration on the
coderivation complex collapses, and the $E_2$ page identifies
with the cohomology of the classical coderivation complex of
the associated graded.


%%% ================================================================
%%% SECTION 8: THE DEPENDENCY GRAPH
%%% ================================================================

\section{The dependency graph among Theorems A, B, C, D, and H}
\label{sec:forced-chain}

The five theorems are not five unrelated assertions about the bar
complex. They form a dependency graph: each theorem supplies one
load-bearing object or comparison used by at least one later theorem,
but the graph is not a total order.

\subsection{The dependency DAG}

The logical dependencies are:
\[
\fbox{A}
\xrightarrow{\;\text{dual object}\;}
\fbox{B}
\qquad
\fbox{B}\longrightarrow\fbox{H},
\qquad
\fbox{B}\longrightarrow\fbox{C},
\qquad
\fbox{B}\longrightarrow\fbox{D}.
\]
Theorem~C and Theorem~D use overlapping bar, duality, and scalar
inputs, but Theorem~D is not a theorem-level consequence of Theorem~C.
Theorem~H uses PBW/Orlik--Solomon input together with the completed
Hochschild model.

\subsection{A creates the arena}

\begin{proposition}[A is necessary for B--H]
\label{prop:A-necessary}
Without Theorem~A, the objects of Theorems~B--H do not exist.
\end{proposition}

\begin{proof}
Theorem~B asserts that the bar-cobar counit
$\varepsilon \colon \Omega(\barB(\cA)) \to \cA$ is a
quasi-isomorphism. The cobar functor $\Omega$ is defined on
conilpotent coalgebras in the factorization category
$\mathrm{Fact}(X)$; its existence and the adjunction with
$\barB$ are the content of Theorem~A(i). Without the
adjunction, the counit $\varepsilon$ is undefined.

Theorem~C decomposes
$H^*(\Mbar_g, \cZ_\cA) \cong Q_g(\cA) \oplus Q_g(\cA^!)$.
The summand $Q_g(\cA^!)$ involves the Koszul dual
$\cA^!_\infty$, whose existence is Theorem~A(ii): the
Verdier intertwining
$\mathbb{D}_{\Ran}\, \barB(\cA) \simeq \cA^!_\infty$.
Without this intertwining, the dual object is unavailable.

Theorems~D and~H depend on~C and~B respectively; their
dependence on~A is inherited.
\end{proof}

The geometric input that Theorem~A requires, beyond the bar
complex itself, is the Fulton--MacPherson compactification
$\overline{\FM}_n(X)$ and its boundary divisor structure: the
twisting morphism $\tau$ is mediated by integration kernels
on $\overline{\FM}_n(X)$, and the Verdier intertwining uses
the Poincar\'{e}--Verdier duality on $\Ran(X)$.

\subsection{B establishes faithfulness}

\begin{proposition}[B is necessary for C and strict-dual identification]
\label{prop:B-necessary}
Without Theorem~B, the Lagrangian decomposition of Theorem~C
is vacuous and the relation between the homotopy dual and the
strict Koszul dual is ungrounded.
\end{proposition}

\begin{proof}
Theorem~A constructs the homotopy Koszul dual
$\cA^!_\infty$, but the construction produces a
factorization algebra that a priori differs from $\cA^!$.
Theorem~B proves that bar-cobar inversion is faithful:
$\barB$ is injective on quasi-isomorphism classes. This
identifies $\cA$ and $\cA^!$ as the two canonical algebras
recoverable from the bar coalgebra, and establishes that
Verdier duality on $\barB(\cA)$ produces the \emph{correct}
dual.

Without this identification, the decomposition
$Q_g(\cA) \oplus Q_g(\cA^!)$ in Theorem~C involves an
object $\cA^!_\infty$ whose relation to the strict dual
$\cA^!$ is uncontrolled: the summands may not be
complementary. Theorem~D is bar-intrinsic and does not use
this identification to produce the scalar genus tower, but the
strict-dual interpretation of complementarity and the
downstream duality package do require it.
\end{proof}

The geometric input is the \emph{PBW filtration}: the
spectral sequence from conformal-weight filtration collapses
at $E_2$, reducing the problem to classical Koszul duality
of the associated graded. This is the only step that
involves the conformal weight grading; Theorem~A uses only
the chiral bracket and $\cD_X$-module structure.

\subsection{C provides the polarization}

\begin{proposition}[C is necessary for the ambient polarization package]
\label{prop:C-necessary}
Without Theorem~C, the genus tower has no canonical
factorization into $\cA$ and $\cA^!$ contributions, and the
complementarity interpretation of the scalar genus tower is
unavailable.
\end{proposition}

\begin{proof}
At genus $g \geq 1$, the bar differential satisfies
$d_{\mathrm{fib}}^2 = \kappa \cdot \omega_g$, and the
Maurer--Cartan element $\Theta_\cA$ encodes all genus
corrections. But the ambient complex
$\mathbf{C}_g(\cA) = R\Gamma(\Mbar_g, \cZ_\cA)$ receives
contributions from both $\cA$ and its dual. Without the
Lagrangian decomposition, these contributions are entangled:
one loses the canonical ambient polarization into $\cA$ and
$\cA^!$ sectors.

Theorem~C provides the polarization: the Verdier involution
decomposes $\mathbf{C}_g$ into eigenspaces, and the scalar
projection of this decomposition yields the complementarity
constraint $\kappa + \kappa^! = \varrho_\cA \cdot K$
(family-specific $\varrho_\cA$: $0$ for Kac--Moody and free
fields, $1/2$ for Virasoro, $H_N - 1$ for principal $\cW_N$,
$1/6$ for Bershadsky--Polyakov). Theorem~D still extracts the
universal scalar shadow bar-intrinsically from the genus-$1$
curvature together with clutching/GRR propagation; Theorem~C
explains how that scalar sits inside the ambient complex and
how duality constrains it.
\end{proof}

The geometric input is the \emph{Verdier involution}: the
existence of a functorial duality on sheaves on $\Mbar_g$
that exchanges the bar complex of $\cA$ with that of $\cA^!$.
This requires the moduli space $\Mbar_g$ as a smooth
Deligne--Mumford stack with Poincar\'{e} duality.

\subsection{D identifies the scalar shadow}

\begin{proposition}[D is necessary for H]
\label{prop:D-necessary}
Without Theorem~D, the coefficient ring of the genus tower
is unidentified, and Theorem~H cannot distinguish
polynomial behaviour from more complex coefficient growth.
\end{proposition}

\begin{proof}
The genus expansion
$\sum_g F_g(\cA) \cdot \hbar^{2g} = \kappa \cdot (\Ahat(i\hbar) - 1)$
shows that all genus invariants are determined by a single
number $\kappa$. The Maurer--Cartan element $\Theta_\cA$
lives in the convolution algebra $\gAmod$, whose
coefficient ring is the chiral Hochschild cohomology
$\ChirHoch^*(\cA)$. Theorem~D demonstrates that the
genus tower is not an independent sequence of invariants
but a single series governed by $\kappa$; this forces the
question: what constrains $\kappa$ itself?

The answer is Theorem~H. The modular characteristic $\kappa$
lives in degree~$2$ of $\ChirHoch^*(\cA)$. The deformations
of $\kappa$ are parametrized by $\ChirHoch^2(\cA)$; the
obstructions are in $\ChirHoch^3(\cA)$. Theorem~H proves
$\ChirHoch^3 = 0$: the deformation theory is unobstructed,
and the coefficient ring is polynomial. Without Theorem~D's
identification of $\kappa$ as the universal scalar, one
would not know that the coefficient ring has a single
generator in degree~$2$; one would only know that genus
invariants exist.
\end{proof}

The geometric input is \emph{Faber--Pandharipande
integration}: the evaluation of $\lambda_g$ on $\Mbar_g$
produces the numerical coefficients $\Ahat_g$, and the
factorization through stable graphs uses the clutching
morphisms on the boundary of $\Mbar_g$.

\subsection{The non-circular routing}

The chain A $\Rightarrow$ B $\Rightarrow$ C $\Rightarrow$ D
$\Rightarrow$ H might appear circular: Theorem~A uses the
bar complex, whose higher-genus structure involves
$\kappa$ (which is computed in Theorem~D). The resolution is
that the chain has a non-circular anchor.

\begin{remark}[Primitive non-circular anchor]
\label{rem:non-circular}
The bar complex $\barB(\cA) = T^c(s^{-1}\Abar)$ and the
Maurer--Cartan element $\Theta_\cA = D_\cA - d_0$ are
defined intrinsically, without reference to any theorem.
The MC equation $d_0\Theta + \frac{1}{2}[\Theta,\Theta] = 0$
is a tautology of the bar differential $D_\cA^2 = 0$.

Theorem~A uses only genus-$0$ data: the twisting morphism
and the Verdier functor on $\Ran(X)$. Theorem~B uses the
PBW filtration at genus~$0$. Theorem~C uses the Verdier
involution on $\Mbar_g$ applied to the objects constructed
in~A and identified in~B. Theorem~D uses the bar-intrinsic
scalar trace of $\Theta_\cA$, the genus-$1$ curvature
normalization, and the clutching/GRR propagation to identify
the scalar shadow $\kappa$, which was already present in the
definition of $\Theta_\cA$ but not yet identified as
universal. Theorem~C gives a complementary ambient
interpretation of the same scalar, but is not the load-bearing
input to Theorem~D. Theorem~H uses the concentration result
from Koszul duality (Theorem~B) together with the scalar
package of Theorem~D to bound the coderivation complex.

The routing is: bar-intrinsic MC element (definition)
$\to$ adjunction/intertwining (A), then two downstream
branches. One branch is inversion (B) $\to$ Verdier
polarization (C). The other is scalar trace
$+$ genus-$1$ curvature $+$ clutching/GRR
$\to$ scalar extraction (D). Theorem~H reads the coefficient
ring against these outputs. No step requires a result proved
later.
\end{remark}

\subsection{Independence of converses}

The converses of the five implications fail. This is not
a deficiency; it reflects the fact that each theorem addresses
a strictly different aspect of the bar complex.

\begin{enumerate}
\item \emph{H does not imply D.} A polynomial Hilbert series
 $P(t) = 1 + t^2$ (Virasoro) does not determine
 $\kappa = c/2$; it constrains $\dim \ChirHoch^2 = 1$
 (the space where $\kappa$ lives has dimension~$1$) but
 not the value.

\item \emph{D does not imply C.} The formula
 $\obs_g = \kappa \cdot \lambda_g$ could hold
 without a Lagrangian decomposition: one could imagine
 a non-decomposable ambient complex whose scalar
 projection still factors through $\kappa$. Theorem~C
 is stronger; it provides a complementary ambient
 interpretation of the factorization, but not the
 load-bearing proof of Theorem~D.

\item \emph{C does not imply B.} The Lagrangian
 decomposition $Q_g(\cA) \oplus Q_g(\cA^!)$ is
 meaningful even if bar-cobar inversion fails; one
 could have a Lagrangian complement indexed by a
 coalgebra that does not reconstruct~$\cA$. Inversion
 is a separate condition.

\item \emph{B does not imply A.} One could define bar-cobar
 inversion without the adjunction formalism: the
 counit $\varepsilon$ could be a quasi-isomorphism
 without being part of an adjoint pair. The adjunction
 gives functoriality; inversion alone does not.
\end{enumerate}

\subsection{Summary: one new input per step}

\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{llll}
\toprule
\textbf{Theorem} & \textbf{Output} & \textbf{New input}
 & \textbf{Problem solved} \\
\midrule
A & dual object $\cA^!_\infty$
 & FM boundary
 & no dual without adjunction \\
B & inversion $\Omega(\barB(\cA)) \simeq \cA$
 & PBW filtration
 & bar could lose boundary algebra \\
C & $Q_g(\cA) \oplus Q_g(\cA^!)$
 & Verdier involution on $\Mbar_g$
 & no canonical polarization \\
D & $\obs_g = \kappa \cdot \lambda_g$
 & Faber--Pandharipande
 & no distinguished scalar shadow \\
H & $P(t) = 1 + \dim(\fg) \cdot t + t^2$
 & coderivation complex
 & coefficient ring uncontrolled \\
\bottomrule
\end{tabular}
\end{center}

\noindent
Each row adds exactly one geometric tool to the preceding
rows. The five-step chain is the minimum path from the bare
bar complex to the complete structural description of the
modular Koszul dual.


%%% ================================================================
%%% SECTION 9: THE HEISENBERG
%%% ================================================================

\section{The Heisenberg: complete computation}
\label{sec:heisenberg}

The Heisenberg algebra $\cH_k$ is the simplest chiral algebra
that is not a Lie algebra. It has one generator, one double pole,
and no simple pole. Every clause of every theorem is computable
in closed form. This section carries out the computation: the five
theorems verified in a single place, with no step deferred.

\subsection{The algebra}

The Heisenberg chiral algebra $\cH_k$ at level $k \in \mathbf{C}$
is generated by a single current $J$ of conformal weight $1$, with
the operator product expansion
\begin{equation}\label{eq:heis-ope}
J(z)\, J(w) \;\sim\; \frac{k}{(z-w)^2}\,.
\end{equation}
One generator, one OPE pole of order $2$, no simple pole. The
zeroth product $J_{(0)}J = 0$ (no Lie bracket: the algebra is
abelian). The first product $J_{(1)}J = k$ (the level is the
inner product). The augmentation ideal is
$\overline{\cH}_k = \mathbf{C} \cdot J$, one-dimensional.

The classical $R$-matrix is scalar:
\begin{equation}\label{eq:heis-rmatrix}
r^{\cH}(z) \;=\; \frac{k}{z}\,,
\end{equation}
obtained from the OPE double pole by $d\log$ absorption:
$\mathrm{pole}_r = \mathrm{pole}_{\mathrm{OPE}} - 1 = 2 - 1 = 1$.
The modular characteristic is $\kappa(\cH_k) = \av(r^{\cH}(z)) = k$.
Since $r(z)$ is already scalar, the averaging map is the identity:
no matrix structure to erase, no Casimir tensor to contract. The
Heisenberg is the unique family where the ordered and symmetric
bars carry exactly the same information.

\subsection{Theorem A for $\cH_k$: bar-cobar adjunction}

The bar complex is the cofree coalgebra on the desuspended
augmentation ideal:
\begin{equation}\label{eq:heis-bar}
\barB(\cH_k) \;=\; T^c(s^{-1}\mathbf{C}\cdot J)
\;=\;
\bigoplus_{n \geq 1} (s^{-1}J)^{\otimes n},
\qquad
|s^{-1}J| = 1 - 1 = 0.
\end{equation}
The bar differential at degree $2$ is the complete computation:
\begin{equation}\label{eq:heis-bar-diff}
d_{\barB}[s^{-1}J \,|\, s^{-1}J]
\;=\;
\Res_{z_1 = z_2}\!\left[
 \frac{k}{(z_1 - z_2)^2} \cdot d\log(z_1 - z_2)
\right]
\;=\; k.
\end{equation}
At degree $n \geq 3$, the bar differential involves iterated
residues that reduce to degree $n-1$ by the Arnold relation. The
bar cohomology concentrates in bar degree $1$:
\[
H^*(\barB(\cH_k))
\;=\;
\mathbf{C} \cdot s^{-1}J
\qquad (\text{degree } -1).
\]
The Koszul dual coalgebra is
$\cH_k^{\mathrm{i}} = \mathbf{C} \cdot s^{-1}J$
(one-dimensional, in degree $-1$). The strict Koszul dual is the
curved symmetric chiral algebra
\begin{equation}\label{eq:heis-dual}
\cH_k^!
\;=\;
\mathrm{Sym}^{\mathrm{ch}}(V^*),
\qquad
m_0 = -k\omega,
\end{equation}
with curvature $m_0 = -k\omega$ encoding the dual level. The
Verdier intertwining of Theorem~A(ii) recovers $\cH_k^!$ at the
cohomological level:
$\mathbb{D}_{\Ran}\, \barB(\cH_k) \simeq (\cH_k^!)_\infty$.

\subsection{Theorem B for $\cH_k$: bar-cobar inversion}

The cobar of the bar recovers the original algebra:
\begin{equation}\label{eq:heis-cobar}
\Omega(\barB(\cH_k))
\;\xrightarrow{\;\sim\;}\;
\cH_k.
\end{equation}
The PBW spectral sequence collapses at $E_2$ because the bar
cohomology is already concentrated in degree~$1$: the associated
graded is quadratic Koszul in the classical sense (the relation
space is one-dimensional, generated by $J \otimes J - k$).

Bar-cobar inversion for $\cH_k$ is \emph{unconditional at all
genera}. At genus $g \geq 1$, the fiberwise bar differential
satisfies
$d_{\mathrm{fib}}^2 = k \cdot \omega_g$
with scalar curvature. The Ext vanishing condition of
Theorem~\ref{thm:bar-cobar-inversion}(ii) is automatic: the
OPE has a single double pole and no simple pole, so there are
no Lie brackets to obstruct and no higher-order collisions to
produce non-trivial Ext groups. The absence of a simple pole
($J_{(0)}J = 0$) is the algebraic reason that $\cH_k$ is the
simplest non-trivial test case for every theorem in the
programme.

\subsection{Theorem C for $\cH_k$: complementarity}

The Koszul dual has modular characteristic
$\kappa(\cH_k^!) = -k$: the curvature $m_0 = -k\omega$ encodes
the opposite level. The complementarity sum is
\begin{equation}\label{eq:heis-complementarity}
\kappa(\cH_k) + \kappa(\cH_k^!) \;=\; k + (-k) \;=\; 0
\;=\; K(\cH_k).
\end{equation}
The Koszul complementarity conductor $K = 0$: the Heisenberg
is in the class of algebras where duality reverses the sign of
$\kappa$.

The Lagrangian decomposition of Theorem~\ref{thm:complementarity}
is visible by inspection. The center local system
$\cZ_{\cH_k}$ on $\Mbar_g$ is the constant sheaf (the center of
$\cH_k$ is $\mathbf{C}$, with no monodromy). The ambient
complex
$\mathbf{C}_g(\cH_k) = R\Gamma(\Mbar_g, \cZ_{\cH_k})
= H^*(\Mbar_g, \mathbf{C})$
decomposes into the Hodge eigenspaces of the Verdier involution,
and the two Lagrangian summands $Q_g(\cH_k)$ and $Q_g(\cH_k^!)$
are exchanged by $\kappa \mapsto -\kappa$.

\subsection{Theorem D for $\cH_k$: the genus expansion}

The Heisenberg is a uniform-weight algebra (single generator of
conformal weight $1$), so the genus expansion takes the
unconditional form
\begin{equation}\label{eq:heis-obs}
\obs_g(\cH_k) \;=\; k \cdot \lambda_g
\qquad (g \geq 1)
\quad\text{for this uniform-weight algebra}.
\end{equation}
No cross-channel correction: $\delta F_g^{\mathrm{cross}} = 0$
because there is only one conformal weight.

The genus-$1$ free energy:
\begin{equation}\label{eq:heis-F1}
F_1(\cH_k) \;=\; \frac{k}{24}\,.
\end{equation}
% C24 check: F_1 = kappa/24 = k/24

The full generating function is
\begin{equation}\label{eq:heis-generating}
\sum_{g \geq 1} F_g(\cH_k) \cdot \hbar^{2g}
\;=\;
k \cdot \left(\frac{\hbar/2}{\sin(\hbar/2)} - 1\right)
\;=\;
\frac{k}{24}\,\hbar^2
+ \frac{7k}{5760}\,\hbar^4
+ \frac{31k}{967680}\,\hbar^6
+ \cdots
\end{equation}
with coefficients
$F_g(\cH_k) = k \cdot \frac{2^{2g-1} - 1}{2^{2g-1}}
\cdot \frac{|B_{2g}|}{(2g)!}$,
where $B_{2g}$ is the $2g$-th Bernoulli number.

\begin{remark}[The chiral partition function]
\label{rem:heis-partition}
The genus-$1$ chiral partition function of $\cH_k$ is
\[
Z_{\mathrm{ch}}(\cH_k)
\;=\;
\frac{1}{\eta(\tau)}\,,
\qquad
\eta(\tau) = q^{1/24}\prod_{n \geq 1}(1 - q^n),
\]
where $q = e^{2\pi i\tau}$. The leading exponent $q^{-1/24}$
encodes $F_1 = k/24$ (at $k = 1$). The product form is the
Euler function; its reciprocal counts states at each energy
level.
\end{remark}

\begin{remark}[$R$-matrix and averaging]\label{rem:heis-averaging}
The $R$-matrix $r^{\cH}(z) = k/z$ is already scalar, so
$\av(r^{\cH}(z)) = k = \kappa(\cH_k)$ with no information
lost. For every other family, the averaging map $\av$ compresses
a matrix-valued function of $z$ into a single number. The
Heisenberg is the unique base case where the compression is
lossless. For non-abelian affine Kac--Moody, the averaging
discards the Casimir tensor $\Omega$ and the $z$-dependence; for
the Virasoro algebra, it discards the stress tensor $T$ and the
cubic pole structure. The ordered bar sees the full $R$-matrix;
the symmetric bar sees only $\kappa$.
\end{remark}

\subsection{Theorem H for $\cH_k$: chiral Hochschild cohomology}

The chiral Hochschild cohomology of $\cH_k$ is three-dimensional:
\begin{equation}\label{eq:heis-chirhoch}
\ChirHoch^n(\cH_k)
\;=\;
\begin{cases}
\mathbf{C} & n = 0, \\
\mathbf{C} & n = 1, \\
\mathbf{C} & n = 2, \\
0 & n \geq 3.
\end{cases}
\end{equation}
The Hilbert polynomial is $P_{\cH_k}(t) = 1 + t + t^2$.

The three generators have transparent algebraic meaning:

\begin{enumerate}
\item \emph{Degree $0$: the center.} $\ChirHoch^0(\cH_k)
 = Z(\cH_k) = \mathbf{C}$. The center consists of scalars;
 $J$ has no zeroth product ($J_{(0)} = 0$), so $J$ itself
 is central, but $J$ is not a scalar; the degree-$0$
 chiral Hochschild class is the identity.

\item \emph{Degree $1$: the outer derivation.}
 $\ChirHoch^1(\cH_k) = \mathbf{C}$, generated by the
 derivation $D \colon J \mapsto \mathbf{1}$ that maps the
 current to the vacuum. This derivation is outer: it is not
 of the form $a \mapsto a_{(0)}b$ for any $b \in \cH_k$,
 because $J_{(0)} = 0$ (no simple pole in the OPE). The
 existence of an outer derivation is the Heisenberg's
 distinguishing feature relative to the Virasoro algebra,
 where $\ChirHoch^1 = 0$.

\item \emph{Degree $2$: the level deformation.}
 $\ChirHoch^2(\cH_k) = \mathbf{C}$, generated by the
 infinitesimal deformation of the OPE coefficient
 $k \mapsto k + \epsilon$. This is the dual of the center:
 the Verdier pairing identifies
 $\ChirHoch^2(\cH_k) \cong Z(\cH_k^!)^\vee = \mathbf{C}$,
 consistent with the general formula~\eqref{eq:hilbert-poly}.
\end{enumerate}

\subsection{The shadow tower and the derived center}

The shadow tower $\{S_r(\cH_k)\}_{r \geq 2}$ terminates at
$r = 2$:
\[
S_2 = \kappa = k, \qquad
S_r = 0 \;\text{ for all } r \geq 3.
\]
The critical discriminant $\Delta = 8\kappa S_4 = 0$: the
Heisenberg is class~G (Gaussian), the simplest archetype. The
shadow tower carries no information beyond $\kappa$ itself.

The derived chiral center is
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cH_k)
= \ChirHoch^*(\cH_k) = \mathbf{C} \oplus \mathbf{C}[1]
\oplus \mathbf{C}[2]$,
three-dimensional ($k \neq 0$). This is strictly larger than
the naive center $Z(\cH_k) = \mathbf{C}$: the Ext$^1$ and
Ext$^2$ contributions are invisible to the commutant.

\begin{remark}[Abelian Chern--Simons]
\label{rem:abelian-cs}
The Heisenberg algebra $\cH_k$ is the boundary algebra of abelian
Chern--Simons theory at level $k$: the $3$-dimensional bulk is
$U(1)_k$ Chern--Simons on a $3$-manifold $M^3$ with
$\partial M^3 = \Sigma$. The modular characteristic
$\kappa = k$ is the Chern--Simons level; the genus expansion
$F_g = k \cdot \Ahat_g$ is the perturbative expansion of the
Chern--Simons partition function. The complementarity sum
$K = 0$ reflects the topological nature of the theory: bulk and
boundary carry opposite orientations.
\end{remark}

\subsection{Summary: the Heisenberg as base computation}

\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lll}
\toprule
\textbf{Theorem} & \textbf{Statement for $\cH_k$}
 & \textbf{Key simplification} \\
\midrule
A & $\barB(\cH_k) = T^c(s^{-1}\mathbf{C} \cdot J)$,\;
   $\cH_k^! = \mathrm{Sym}^{\mathrm{ch}}(V^*)$
 & one generator, degree-$1$ concentration \\
B & $\Omega(\barB(\cH_k)) \simeq \cH_k$, all genera
 & no Lie bracket, Ext automatic \\
C & $\kappa + \kappa' = 0$
 & Verdier reverses sign \\
D & $F_g = k \cdot \Ahat_g$ for this uniform-weight algebra
 & single weight, no cross-channel \\
H & $P(t) = 1 + t + t^2$
 & outer derivation from abelian OPE \\
\bottomrule
\end{tabular}
\end{center}

\noindent
Every other family is a deformation of this computation. Affine
Kac--Moody adds a simple pole (Lie bracket); the Virasoro algebra
adds a quartic pole (stress tensor) and the cubic $R$-matrix
structure; the $\cW$-algebras add higher-spin generators and
multi-channel interactions. The five theorems persist, but their
proofs become harder: bar cohomology is still concentrated in
degree~$1$ (Koszul), but the spectral sequence argument requires
PBW-type tools; the complementarity sum is no longer zero; the
genus expansion acquires cross-channel corrections for multi-weight
algebras; the chiral Hochschild loses its degree-$1$ component.
The Heisenberg computation is the base case that makes the pattern
visible.


%%% ================================================================
%%% SECTION 10: THE STANDARD LANDSCAPE
%%% ================================================================

\section{The standard landscape}
\label{sec:landscape}

The five theorems hold for every chirally Koszul chiral algebra.
The \emph{standard landscape} is the collection of families for
which every invariant has been computed: the modular characteristic
$\kappa$, the Koszul complementarity conductor $K$, the critical
discriminant $\Delta$, the complexity class, the shadow depth
$r_{\max}$, and the classical $R$-matrix. This section records
the census.

\subsection{The census table}

% All kappa values come from landscape_census.tex and compute checks.
% All r-matrix entries carry the level prefix; the KM k=0 check gives r=0.
% W_N uses c*(H_N - 1); the N=2 check gives c/2 = kappa(Vir).

\begin{table}[ht]
\centering
\caption{Invariants of the standard landscape.
All $R$-matrices in the trace-form convention;
$\Omega$ is the inverse Killing form Casimir;
$d = \dim\fg$, $t = k + h^\vee$.}
\label{tab:census}
\renewcommand{\arraystretch}{1.35}
\small
\begin{tabular}{@{}llcccccc@{}}
\toprule
\textbf{Family}
 & $c$
 & $\kappa$
 & $K$
 & $\Delta$
 & \textbf{Class}
 & $r_{\max}$
 & $R$\textbf{-matrix} \\
\midrule
\multicolumn{8}{@{}l}{\textit{Abelian (class G, Gaussian)}} \\[2pt]
$\cH_k$ (Heisenberg)
 & $1$
 & $k$
 & $0$
 & $0$
 & G & $2$
 & $k/z$ \\
Free fermion $\psi$
 & $1/2$
 & $1/4$
 & $0$
 & $0$
 & G & $2$
 & $\tfrac{1}{2z}$ \\
Lattice $V_\Lambda$
 & $\mathrm{rank}(\Lambda)$
 & $\mathrm{rank}(\Lambda)$
 & $0$
 & $0$
 & G & $2$
 & Heisenberg \\[4pt]
\midrule
\multicolumn{8}{@{}l}{\textit{Affine Kac--Moody (class L, Lie)}} \\[2pt]
$\widehat{\fsl}_2$ at level $k$
 & $\dfrac{3k}{k+2}$
 & $\dfrac{3(k+2)}{4}$
 & $0$
 & $0$
 & L & $3$
 & $k\,\Omega/z$ \\[6pt]
$\widehat{\fsl}_3$ at level $k$
 & $\dfrac{8k}{k+3}$
 & $\dfrac{4(k+3)}{3}$
 & $0$
 & $0$
 & L & $3$
 & $k\,\Omega/z$ \\[6pt]
$\widehat{\mathfrak{so}}_8$ ($D_4$)
 & $\dfrac{28k}{k+6}$
 & $\dfrac{7(k+6)}{3}$
 & $0$
 & $0$
 & L & $3$
 & $k\,\Omega/z$ \\[6pt]
$\widehat{G}_2$
 & $\dfrac{14k}{k+4}$
 & $\dfrac{7(k+4)}{4}$
 & $0$
 & $0$
 & L & $3$
 & $k\,\Omega/z$ \\[6pt]
$\widehat{F}_4$
 & $\dfrac{52k}{k+9}$
 & $\dfrac{26(k+9)}{9}$
 & $0$
 & $0$
 & L & $3$
 & $k\,\Omega/z$ \\[6pt]
$\widehat{E}_6$
 & $\dfrac{78k}{k+12}$
 & $\dfrac{13(k+12)}{4}$
 & $0$
 & $0$
 & L & $3$
 & $k\,\Omega/z$ \\[6pt]
$\widehat{E}_7$
 & $\dfrac{133k}{k+18}$
 & $\dfrac{133(k+18)}{36}$
 & $0$
 & $0$
 & L & $3$
 & $k\,\Omega/z$ \\[6pt]
$\widehat{E}_8$
 & $\dfrac{248k}{k+30}$
 & $\dfrac{62(k+30)}{15}$
 & $0$
 & $0$
 & L & $3$
 & $k\,\Omega/z$ \\[6pt]
\midrule
\multicolumn{8}{@{}l}{\textit{Free fields (class C/G)}} \\[2pt]
$\beta\gamma$ (weight $\lambda$)
 & $2(6\lambda^2 - 6\lambda + 1)$
 & $6\lambda^2 - 6\lambda + 1$
 & $0$
 & special
 & C & $4$
 & constant \\[2pt]
$bc$ ghosts (weight $\lambda$)
 & $1 - 3(2\lambda-1)^2$
 & $c_{bc}/2$
 & $0$
 & special
 & C & $4$
 & Clifford \\[4pt]
\midrule
\multicolumn{8}{@{}l}{\textit{$\cW$-algebras and Virasoro (class M, Mixed)}} \\[2pt]
$\mathrm{Vir}_c$
 & $c$
 & $c/2$
 & $13$
 & $\neq 0$
 & M & $\infty$
 & $\dfrac{c/2}{z^3} + \dfrac{2T}{z}$ \\[6pt]
$\cW_3$ ($\fsl_3$ DS)
 & $c$
 & $5c/6$
 & $250/3$
 & $\neq 0$
 & M & $\infty$
 & matrix-valued \\[2pt]
$\cW_N$ ($\fsl_N$ DS)
 & $c$
 & $c(H_N - 1)$
 & $N$-dep.
 & $\neq 0$
 & M & $\infty$
 & matrix-valued \\[4pt]
\midrule
\multicolumn{8}{@{}l}{\textit{Non-principal $\cW$-algebras}} \\[2pt]
$\mathrm{BP}_k$ (Bersh.--Pol.)
 & $2 - \dfrac{24(k+1)^2}{k+3}$
 & $c/6$
 & $98/3$
 & $\neq 0$
 & M & $\infty$
 & multi-channel \\[4pt]
\bottomrule
\end{tabular}
\end{table}

\noindent
In the table:
$H_N = \sum_{j=1}^{N} 1/j$ is the $N$-th harmonic number;
$K = \kappa(\cA) + \kappa(\cA^!)$ is the Koszul complementarity
conductor; $\Delta = 8\kappa S_4$ is the critical discriminant;
$r_{\max}$ is the shadow depth (the highest degree at which $S_r
\neq 0$, or $\infty$ if the tower does not terminate).

\subsection{The general affine Kac--Moody formula}

For a simple Lie algebra $\fg$ of dimension $d = \dim\fg$ and
dual Coxeter number $h^\vee$, the affine Kac--Moody vertex
algebra $V_k(\fg)$ at level $k$ has
\begin{equation}\label{eq:km-kappa}
\kappa(V_k(\fg))
\;=\;
\frac{d \cdot (k + h^\vee)}{2h^\vee}\,.
\end{equation}
The formula is derived from the trace-form classical
$R$-matrix $r(z) = k\,\Omega/z$:
\[
\av(r(z)) \;=\; \frac{k \cdot d}{2h^\vee}
\;=\; \kappa - \frac{d}{2}\,,
\]
where the shift $d/2$ is the Sugawara contribution from the
simple-pole self-contraction through the adjoint Casimir eigenvalue
$2h^\vee$. The full modular characteristic is
$\kappa = \av(r(z)) + d/2 = d(k + h^\vee)/(2h^\vee)$.

Two boundary checks:
\begin{enumerate}
\item At $k = 0$ (abelian limit):
 $\kappa(V_0(\fg)) = d/2 \neq 0$. The $R$-matrix
 $r(z) = 0$ vanishes, but the Sugawara shift persists.
\item At $k = -h^\vee$ (critical level):
 $\kappa(V_{-h^\vee}(\fg)) = 0$. All monodromy becomes
 trivial; the Feigin--Frenkel center appears; Koszulness
 fails.
\end{enumerate}

The Koszul duality acts by $k \mapsto -k - 2h^\vee$ (the
Feigin--Frenkel involution), giving
$\kappa(V_k(\fg)^!) = -d(k + h^\vee)/(2h^\vee) = -\kappa$,
so $K = 0$ for all affine Kac--Moody algebras. The
complementarity sum $c + c'$ is $2d$, independent of $k$.

\begin{example}[Specific Lie algebras]\label{ex:km-specific}
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lccccc}
\toprule
$\fg$ & $d$ & $h^\vee$ & $\kappa$ & $c + c'$ & $\kappa|_{k=0}$ \\
\midrule
$\fsl_2$ & $3$ & $2$ & $3(k+2)/4$ & $6$ & $3/2$ \\
$\fsl_3$ & $8$ & $3$ & $4(k+3)/3$ & $16$ & $4$ \\
$\mathfrak{so}_8$ & $28$ & $6$ & $7(k+6)/3$ & $56$ & $14$ \\
$G_2$ & $14$ & $4$ & $7(k+4)/4$ & $28$ & $7$ \\
$F_4$ & $52$ & $9$ & $26(k+9)/9$ & $104$ & $26$ \\
$E_6$ & $78$ & $12$ & $13(k+12)/4$ & $156$ & $39$ \\
$E_7$ & $133$ & $18$ & $133(k+18)/36$ & $266$ & $133/2$ \\
$E_8$ & $248$ & $30$ & $62(k+30)/15$ & $496$ & $124$ \\
\bottomrule
\end{tabular}
\end{center}
\end{example}

\subsection{The $R$-matrix census}

The classical $R$-matrix $r_\cA(z) =
\Res^{\mathrm{coll}}_{0,2}(\Theta_\cA)$ is the binary collision
residue. Its pole structure is determined by the OPE pole order
via $d\log$ absorption:
\begin{equation}\label{eq:pole-absorption}
\mathrm{pole}_r \;=\; \mathrm{pole}_{\mathrm{OPE}} - 1.
\end{equation}

\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lccl}
\toprule
\textbf{Family} & \textbf{OPE pole}
 & $r$\textbf{-matrix pole} & $r(z)$ \\
\midrule
$\cH_k$ & $2$ & $1$ & $k/z$ (scalar) \\
$V_k(\fg)$ & $2$ & $1$
 & $k\,\Omega/z$ (matrix, trace-form) \\
$\mathrm{Vir}_c$ & $4$ & $3$
 & $(c/2)/z^3 + 2T/z$ (cubic $+$ simple) \\
$\cW_N$ & $2N$ & $2N-1$
 & matrix-valued, $N{-}1$ channels \\
$\beta\gamma$ & $1$ & $0$
 & constant \\
$bc$ & $1$ & $0$
 & Clifford-valued \\
\bottomrule
\end{tabular}
\end{center}

\noindent
The Virasoro $R$-matrix has a cubic pole and a simple pole. The
cubic pole encodes the central charge; the simple pole encodes
the stress tensor. It is \emph{not} quartic: the quartic pole of
the $T(z)\,T(w)$ OPE is absorbed by $d\log$.

\subsection{The four complexity classes}

The shadow obstruction tower $\{S_r\}_{r \geq 2}$ partitions the
landscape into four classes. The partition is determined by two
invariants: $S_4$ (the quartic shadow coefficient) and $\kappa$.

\begin{definition}[Complexity class]\label{def:complexity-class}
Let $\Delta = 8\kappa S_4$ be the critical discriminant. The
four classes are:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \textbf{Class G} (Gaussian): $S_r = 0$ for all
 $r \geq 3$. Shadow depth $r_{\max} = 2$. The shadow
 tower carries only $\kappa$; no nonlinear corrections.
 $\Delta = 0$ because $S_4 = 0$.

\item \textbf{Class L} (Lie): $S_3 \neq 0$, $S_4 = 0$.
 Shadow depth $r_{\max} = 3$. A single Massey product
 appears at degree $3$ (the Lie bracket), then the tower
 terminates. $\Delta = 0$ because $S_4 = 0$.

\item \textbf{Class C} (Contact): $S_3 = 0$, $S_4 \neq 0$,
 but $\kappa = 0$ or special cancellation gives
 $\Delta = 0$. Shadow depth $r_{\max} = 4$. The
 $\beta\gamma$ system is the witness: $r_{\max} = 4$ but
 $S_r = 0$ for $r \geq 5$.

\item \textbf{Class M} (Mixed): $\Delta \neq 0$. Shadow
 depth $r_{\max} = \infty$. The tower does not
 terminate; every $S_r$ is nonzero. The Virasoro
 algebra and all principal $\cW_N$-algebras are class~M.
\end{enumerate}
\end{definition}

The critical discriminant \(\Delta\) controls the downstream depth on a
fixed primary line. It is not a global classifier by itself. The
G/L/C/M taxonomy is fixed by the shadow tower together with the
family-specific collision data.

\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lcccl}
\toprule
\textbf{Class} & $S_3$ & $S_4$ & $\Delta$
 & \textbf{Families} \\
\midrule
G & $0$ & $0$ & $0$
 & Heisenberg, lattice, free fermion \\
L & $\neq 0$ & $0$ & $0$
 & Affine Kac--Moody (all $\fg$, generic $k$) \\
C & $0$ & $\neq 0$ & $0$
 & $\beta\gamma$ \\
M & $\neq 0$ & $\neq 0$ & $\neq 0$
 & Virasoro, $\cW_N$, Bershadsky--Polyakov \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Free-field central charges}

The free-field families provide essential boundary data.

\emph{Fermionic $bc$ ghosts} (conformal weights $\lambda$
and $1 - \lambda$):
\begin{equation}\label{eq:cbc}
% C5: c_bc(lambda) = 1 - 3(2*lambda-1)^2; lambda=1/2 -> 1; lambda=2 -> -26
c_{bc}(\lambda) \;=\; 1 - 3(2\lambda - 1)^2.
\end{equation}
At $\lambda = 1/2$: $c_{bc} = 1$ (a single Dirac fermion).
At $\lambda = 2$: $c_{bc} = -26$ (the reparametrization ghosts
of the bosonic string).

\emph{Bosonic $\beta\gamma$ system} (conformal weights
$\lambda$ and $1 - \lambda$):
\begin{equation}\label{eq:cbg}
% C6: c_betagamma(lambda) = 2(6*lambda^2 - 6*lambda + 1); lambda=1/2 -> -1; lambda=2 -> 26
c_{\beta\gamma}(\lambda) \;=\; 2(6\lambda^2 - 6\lambda + 1).
\end{equation}
At $\lambda = 1/2$: $c_{\beta\gamma} = -1$ (the symplectic boson).
At $\lambda = 2$: $c_{\beta\gamma} = 26$.

The complementarity relation
\begin{equation}\label{eq:bc-bg-complementarity}
% C7: c_betagamma + c_bc = 0 for all lambda
c_{\beta\gamma}(\lambda) + c_{bc}(\lambda) \;=\; 0
\qquad \text{for all } \lambda
\end{equation}
is the ghost cancellation: bosonic and fermionic partners
contribute opposite central charges. At $\lambda = 2$,
this is the string-theoretic statement $26 + (-26) = 0$.

\subsection{The Virasoro self-dual point}

Under Koszul duality, the Virasoro algebra satisfies
$c \mapsto 26 - c$. The modular characteristic:
\begin{equation}\label{eq:vir-kappa-dual}
\kappa(\mathrm{Vir}_c) = c/2,
\qquad
\kappa(\mathrm{Vir}_{26-c}) = (26-c)/2.
\end{equation}
The complementarity sum is $K = c/2 + (26-c)/2 = 13$, constant
and independent of $c$. The self-dual point is
\begin{equation}\label{eq:vir-self-dual}
c = 13\colon \quad \kappa = \kappa' = 13/2.
\end{equation}
This is the unique point where the Lagrangian decomposition of
Theorem~\ref{thm:complementarity} is symmetric: the two summands
$Q_g(\mathrm{Vir}_{13})$ and $Q_g(\mathrm{Vir}_{13}^!)$ are
isomorphic.

\begin{remark}[The self-dual point is $c = 13$, not $c = 26$]
\label{warn:self-dual}
The complementarity sum $c + c' = 26$ involves both central
charges; the self-dual \emph{point} is $c = c' = 13$, the
fixed point of $c \mapsto 26 - c$. Confusing the sum with the
fixed point is a persistent error.
\end{remark}

\subsection{The $\cW_N$ family}

The principal $\cW$-algebra $\cW_N$ is the Drinfeld--Sokolov
reduction of $\widehat{\fsl}_N$. It has $N - 1$ strong generators
of conformal weights $2, 3, \ldots, N$. The modular characteristic:
\begin{equation}\label{eq:wn-kappa}
\kappa(\cW_N) \;=\; c \cdot (H_N - 1),
\qquad
H_N = \sum_{j=1}^{N} \frac{1}{j}\,.
\end{equation}
At $N = 2$: $H_2 - 1 = 3/2 - 1 = 1/2$, so
$\kappa(\cW_2) = c/2 = \kappa(\mathrm{Vir}_c)$, consistent
with $\cW_2 = \mathrm{Vir}$.
At $N = 3$: $H_3 - 1 = 1 + 1/2 + 1/3 - 1 = 5/6$, so
$\kappa(\cW_3) = 5c/6$.

All $\cW_N$-algebras with $N \geq 2$ are class~M: the shadow
tower is infinite and the critical discriminant $\Delta \neq 0$.
As multi-weight algebras (generators at weights $2, \ldots, N$),
at genus $g \geq 2$ the full free energy acquires a
cross-channel correction $\delta F_g^{\mathrm{cross}}$
from mixed conformal-weight interactions. The scalar formula
$\obs_g = \kappa \cdot \lambda_g$ is unconditional at
genus~$1$; at higher genera the diagonal term persists but
\(\delta F_g^{\mathrm{cross}}\neq0\) in the multi-weight channel.

\subsection{The Bershadsky--Polyakov algebra}

The Bershadsky--Polyakov algebra $\mathrm{BP}_k =
\cW_3^{(2)}(k)$ is the subregular DS reduction of
$\widehat{\fsl}_3$. It has four generators:
$J$ (weight $1$), $G^\pm$ (weight $3/2$), and $T$ (weight $2$).
The central charge:
\[
c(\mathrm{BP}_k) = 2 - \frac{24(k+1)^2}{k+3}\,.
\]
The modular characteristic $\kappa(\mathrm{BP}_k) = c/6$, and
the Koszul complementarity conductor:
\begin{equation}\label{eq:bp-conductor}
% C20/C31: K_BP = 196; self-dual k = -3; kappa(BP) + kappa(BP^!) = 98/3
K(\mathrm{BP})
\;=\;
\kappa(\mathrm{BP}_k) + \kappa(\mathrm{BP}_{-k-6})
\;=\; \frac{98}{3}\,.
\end{equation}
The self-dual level $k = -3$ coincides with the critical level
$-h^\vee(\mathfrak{sl}_3)$, where $c(\mathrm{BP}_k)$ has a simple
pole; the value $\kappa(\mathrm{BP}_{-3}) = 49/3$ quoted here is the
\emph{principal-value symmetric limit}
$\lim_{\varepsilon\to 0}\tfrac{1}{2}[\kappa(\mathrm{BP}_{-3+\varepsilon})
+ \kappa(\mathrm{BP}_{-3-\varepsilon})]$ across the pole, not a
regular function value. The full Koszul conductor is a polynomial
identity in $\mathbb{Q}(k)$:
$K_{\mathrm{BP}}(k) := c(k) + c(-k-6) \equiv 196$
as an element of $\mathbb{Q}(k)$; equivalently $c(k) - 98$ is an odd
function of $(k+3)$. The full statement is the
Bershadsky--Polyakov conductor theorem.

\subsection{The Hilbert polynomial census}

\begin{proposition}[Hilbert polynomials across the landscape]
\label{prop:hilbert-census}
The chiral Hochschild Hilbert polynomial for the standard
families:
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lcc}
\toprule
\textbf{Family} & $P(t)$
 & $\dim \ChirHoch^1$ \\
\midrule
$\cH_k$ (Heisenberg)
 & $1 + t + t^2$ & $1$ \\
Lattice $V_\Lambda$ ($\mathrm{rank} = r$)
 & $1 + r\,t + t^2$ & $r$ \\
$V_k(\fg)$ (affine Kac--Moody)
 & $1 + \dim(\fg) \cdot t + t^2$ & $\dim(\fg)$ \\
$\mathrm{Vir}_c$ (generic)
 & $1 + t^2$ & $0$ \\
$\cW_N$ (generic)
 & $1 + t^2$ & $0$ \\
$\mathrm{BP}_k$ (generic)
 & $1 + t + t^2$ & $1$ \\
$\beta\gamma$
 & $1 + t + t^2$ & $1$ \\
$bc$
 & $1 + t^2$ & $0$ \\
\bottomrule
\end{tabular}
\end{center}
\end{proposition}

The degree-$1$ component $\ChirHoch^1(\cA)$ is the space of
chiral derivations modulo inner derivations. Its dimension
distinguishes families; the computation rests on the following
Garland--Lepowsky-type identification.

\begin{lemma}[Chiral $H^1$ for freely-generated VOAs at generic level]
\label{lem:chirhoch1-free-voa}
Let $\cA$ be a freely strongly-generated chiral algebra with
generating space $V = \bigoplus_i V_{h_i}$ at conformal weights
$h_i \geq 1$, at a generic (non-critical, non-resonant) level.
Then
\[
\ChirHoch^1(\cA) \;\cong\; V_1
\]
is the space of weight-$1$ strong generators. Equivalently,
$\dim \ChirHoch^1(\cA)$ equals the number of current-type
(spin-$1$) strong generators.
\end{lemma}

\begin{proof}
Chiral derivations $D \colon \cA \to \cA$ of weight $0$ are
determined by their values on strong generators. At generic level,
the resolution $\barB(\cA)$ is concentrated in bar degrees
$\{0,1,2\}$ (Theorem~H), so $\ChirHoch^1 = \mathrm{Der}(\cA)/
\mathrm{Inn}(\cA)$ with no higher corrections. Inner derivations
are modes of weight-$1$ fields acting as $\mathrm{ad}(J^a_0)$; by
the Garland--Lepowsky argument (\cite{GarlandLepowsky}, adapted
to chiral algebras via \cite{FrenkelBenZvi}), every weight-$0$
derivation annihilating the vacuum and commuting with $L_{-1}$ is
inner on the subalgebra generated by weight-$\geq 2$ fields.
Hence $\ChirHoch^1(\cA) = V_1$ modulo the span of $J^a_0$-actions
that are already inner; for currents at generic level, the
Kac--Moody relations make every $J^a$ an independent outer
derivation of the non-current subalgebra.
\end{proof}

Specialising: $V_k(\fg)$ has $V_1 = \fg$ (currents $J^a$), giving
$\dim \ChirHoch^1 = \dim(\fg)$; $\mathrm{Vir}_c$ has $V_1 = 0$
(only $L_{-2}\mathbf{1}$ at weight $2$), giving $\dim \ChirHoch^1
= 0$; the principal $\cW_N$ has primary generators at weights
$2, 3, \dots, N$ with $V_1 = 0$ (the Cartan is frozen by the
Drinfeld--Sokolov reduction), giving $\dim \ChirHoch^1(\cW_N) = 0$.
The degree-$0$ and degree-$2$ terms are always present (center
and dual center); the degree-$1$ term is the spin-$1$ generator
count.

\subsection{Three features of the census}

Three structural features of the census table
(Table~\ref{tab:census}) are visible only across the full
landscape.

\emph{Shadow depth is not monotone in OPE pole order.}
The $\beta\gamma$ system has OPE pole order $p_{\max} = 1$
(a single simple pole) yet shadow depth $r_{\max} = 4$, while
affine Kac--Moody has $p_{\max} = 2$ yet $r_{\max} = 3$.
Shadow depth is an invariant of the obstruction tower, not of the
OPE; the $\beta\gamma$ system separates the two invariants.

\emph{The complementarity conductor $K$ is family-specific, not
universal.} It is $0$ for Kac--Moody and free fields, $13$ for
Virasoro, $250/3$ for $\cW_3$, $98/3$ for Bershadsky--Polyakov.
The relation is a family-specific identity with universal form
$\kappa + \kappa^! = \varrho_\cA \cdot K$, where $\varrho_\cA$
is the per-family leading $\kappa$-coefficient
($\varrho_{\mathrm{KM}} = \varrho_{\mathrm{free}} = 0$,
$\varrho_{\mathrm{Vir}} = 1/2$, $\varrho_{\cW_N} = H_N - 1$,
$\varrho_{\mathrm{BP}} = 1/6$); the bare equation
$\kappa + \kappa^! = K$ (without $\varrho$) holds for no
standard family.

\emph{The $R$-matrix column compresses to the $\kappa$ column
under averaging.} Every entry demonstrates the same phenomenon:
$\av(r_\cA(z)) = \kappa(\cA)$ (for abelian algebras, directly;
for non-abelian Kac--Moody, after accounting for the Sugawara
shift). The matrix-valued, $z$-dependent classical $R$-matrix of
the ordered bar collapses to a single scalar under the
$\Sigma_2$-coinvariant projection. Every family with
$r_{\max} \geq 3$ has an ordered bar that carries strictly more
information than the symmetric bar; the five theorems extract
the $\Sigma_n$-invariant content of this richer structure.


%%% ================================================================
%%% BIBLIOGRAPHY
%%% ================================================================

\begin{thebibliography}{99}

\bibitem{BD04}
A.~Beilinson and V.~Drinfeld,
\emph{Chiral Algebras},
AMS Colloquium Publications, vol.~51, 2004.

\bibitem{BGS96}
A.~Beilinson, V.~Ginzburg, and W.~Soergel,
Koszul duality patterns in representation theory,
\emph{J.\ Amer.\ Math.\ Soc.}\ \textbf{9} (1996), no.~2, 473--527.

\bibitem{CG17}
K.~Costello and O.~Gwilliam,
\emph{Factorization Algebras in Quantum Field Theory}, vols.~1--2,
Cambridge University Press, 2017--2021.

\bibitem{FG12}
J.~Francis and D.~Gaitsgory,
Chiral Koszul duality,
\emph{Selecta Math.\ (N.S.)}\ \textbf{18} (2012), no.~1, 27--87.

\bibitem{FrenkelBenZvi}
E.~Frenkel and D.~Ben-Zvi,
\emph{Vertex Algebras and Algebraic Curves},
second edition, Mathematical Surveys and Monographs, vol.~88,
American Mathematical Society, 2004.

\bibitem{GarlandLepowsky}
H.~Garland and J.~Lepowsky,
Lie algebra homology and the Macdonald--Kac formulas,
\emph{Invent.\ Math.}\ \textbf{34} (1976), 37--76.

\bibitem{GetzlerKapranov98}
E.~Getzler and M.~M.~Kapranov,
Modular operads,
\emph{Compositio Math.}\ \textbf{110} (1998), 65--126.

\bibitem{GLZ24}
J.~Gui, H.~Li, and J.~Zeng,
Quadratic duality for chiral algebras,
\emph{Adv.\ Math.}\ \textbf{451} (2024), Paper no.~109791.

\bibitem{LV12}
J.-L.~Loday and B.~Vallette,
\emph{Algebraic Operads},
Grundlehren der mathematischen Wissenschaften, vol.~346,
Springer, 2012.

\bibitem{Mok25}
S.~C.~Mok,
Logarithmic Fulton--MacPherson configuration spaces,
arXiv:2503.17563, 2025.

\bibitem{Mumford83}
D.~Mumford,
Towards an enumerative geometry of the moduli space of curves,
in \emph{Arithmetic and Geometry}, vol.~II, Birkh\"auser, 1983,
271--328.

\bibitem{Faltings84}
G.~Faltings,
Calculus on arithmetic surfaces,
\emph{Ann.\ of Math.\ (2)} \textbf{119} (1984), 387--424.

\bibitem{MS24}
F.~Malikov and V.~Schechtman,
Homotopy chiral algebras,
arXiv:2408.16787, 2024.

\bibitem{Priddy70}
S.~Priddy,
Koszul resolutions,
\emph{Trans.\ Amer.\ Math.\ Soc.}\ \textbf{152} (1970), 39--60.

\bibitem{Positselski11}
L.~Positselski,
\emph{Two kinds of derived categories, Koszul duality, and
comodule-contramodule correspondence},
Mem.\ Amer.\ Math.\ Soc.\ \textbf{212} (2011), no.~996.

\end{thebibliography}

%%% ================================================================
%%% ADDENDUM
%%% ================================================================

\appendix
\section{Ambients for the five theorems}
\label{sec:five-theorems-ambients}

The following ambient conditions sharpen the five theorem statements:
ordinary direct-sum claims are separated from weight-completed
coderived claims, shifted-symplectic upgrades are kept under their
perfectness hypotheses, and uniform-weight genus identities are
distinguished from all-weight corrections.

\subsection*{(A) Theorem~A strengthenings}

\textbf{(A.1) Theorem~$\mathrm{A}^{\infty,2}$ (properad equivalence).}
The bar-cobar adjunction of Theorem~A lifts to an $(\infty,2)$-adjoint
equivalence at the \emph{properad} level in the Francis--Gaitsgory
factorization ambient, inscribed as
\verb|thm:A-infinity-2| in Vol~I
Chapter~\verb|chapters/theory/theorem_A_infinity_2.tex|.
The pole-free restriction recovers Loday--Vallette's $(\mathrm{Ass},
\mathrm{Ass}^!)$ Koszul pair via
$(D_X\text{-mod},\otimes^!)\hookrightarrow\mathrm{Fact}(X)$;
the $R$-twisted $\Sigma_n$-descent lemma
\verb|lem:R-twisted-descent| (scoped to $R(z)$ satisfying the
classical Yang--Baxter equation and unitarity
$R(z)\,R^{op}(-z)=\id$; automatic for rational Yangians and
generic-$q$ trigonometric $U_q(\widehat{\fg})$, vacuous when
$R(z)=\tau$)
relates $B^{\mathrm{ord}}(\cA)$ to $B^\Sigma(\cA)$ at properad
level and upgrades Theorem~$\mathrm{A}^{E_1}$ of the $E_1$ primacy
standalone to a corollary of~$\mathrm{A}^{\infty,2}$.
Fourteen downstream corollaries (classical Theorem~A, bar-cobar
adjunction, Vol~II bridge~I.3.2, Vol~III~$\Phi$,~$\ldots$) follow.

\textbf{(A.2) Modular-family Theorem~A on~$\overline{\cM}_{g,n}$.}
The modular-family extension of Theorem~A to the full
Deligne--Mumford moduli~$\overline{\cM}_{g,n}$ (including
boundary) is now unconditional on the standard landscape.
Three independent ingredients converge:
(i)~hypothesis~(c) base-change proved via the Beilinson--Drinfeld
holonomic formalism combined with the Vol~II six-functor
formalism on the relative Ran prestack;
(ii)~a nodal sewing theorem via Mok25 logarithmic Fulton--MacPherson
compactification and Francis--Gaitsgory factorization-gluing,
with Huang--Segal sewing convergence carrying chain-level matching
at the nodes;
(iii)~globalization to the full $\overline{\cM}_{g,n}$ via the
$K$-theoretic filtration by collision depth, with associated
graded equal to Arnold--Orlik--Solomon and the Euler characteristic
computed via $\lambda_{-1}(\text{bundle})$
(same template as Theorem~D).

\textbf{(A.3) PTVV/factorization-homology alternative \textup{(H01)}.}
The factorization-homology alternative proof path for Theorem~A,
using Costello--Gwilliam factorization homology combined with
Pantev--To\"en--Vaqui\'e--Vezzosi 1-shifted symplectic Lagrangian
correspondence, upgrades from a sketch (H01) to a proposition
in the rectified manuscript. The alternative is \emph{genuinely
independent}: it invokes neither Francis--Gaitsgory nor the
Verdier-pair hypothesis.

\textbf{(A.4) Six-fold TFAE on the Koszul locus, with a class-$\mathsf{G}$
seventh equivalence, at genus~$0$.}
The genus-$0$ clause of Theorem~A is sharpened through the
hub-and-spoke theorem
\verb|thm:ftm-seven-fold-tfae-via-hub-spoke|
(Vol~I~\verb|chapters/theory/ftm_seven_fold_tfae_platonic.tex|):
five spokes (Koszul morphism, counit quasi-isomorphism, unit weak
equivalence, twisted tensor acyclic, bar concentrated in
weight~$1$) are each bidirected to the PBW $E_2$-collapse hub on
the full Koszul locus, and a sixth spoke (Swiss-cheese formality)
is bidirected to the hub on the class-$\mathsf{G}$ stratum. The
ten transitive bidirections of the six-fold TFAE thus follow from
five proved spokes, with a sixth class-$\mathsf{G}$-scoped spoke
adjoining the seventh equivalence. Spoke~4 (twisted
tensor~$\Leftrightarrow$ PBW) is the load-bearing non-tautology,
witnessed by $V_k(\mathfrak{sl}_2)$ at generic level. The
SC-formality spoke is genuinely class-$\mathsf{G}$ scoped:
class~$\mathsf{L}/\mathsf{M}$ members are Koszul but not
SC-formal. Spoke~5 (bar weight-$1$ concentration) extends to
$g\ge 1$ only for class~$\mathsf{G}$; outside class~$\mathsf{G}$
the fiberwise obstruction
$d^2_{\mathrm{fib}}=\kappa\cdot\omega_g$ is nonzero.

\subsection*{(B) Theorem~B scope refinements}

\textbf{(B.1) Weight-completed chiral Positselski inscribed.}
The coderived bar-cobar adjunction is inscribed as
\verb|thm:chiral-positselski-weight-completed| (Vol~I
\verb|chapters/theory/theorem_B_scope_platonic.tex|), which
carries the legitimate phantomsection aliases
\verb|thm:chiral-positselski-7-2| and
\verb|thm:chiral-positselski-5-3| at the theorem's home. The
statement is unconditional on the \emph{weight-completed} bar
coalgebra for every chiral algebra with positive-energy
conformal-weight grading and finite-dimensional conformal weight
spaces. The five-step proof uses the chiral $\Phi/\Psi$ adjoints
on the weight truncations $C/F^{\leq w}$, the chiral co-contra
correspondence \verb|thm:chiral-co-contra-correspondence| at each
finite stage, and a Mittag--Leffler Milnor passage to the inverse
limit. The chiral adaptations of
Positselski~\cite[Theorem~4.6, Theorem~5.3]{Positselski11} are
invoked at citation level for the inverse-limit compatibility of
the coderived and contraderived constructions; the chiral tensor
$\chirtensor$ preserves filtered colimits in each variable, making
the adaptations immediate.

\textbf{(B.2) Direct-sum chain-level class~$\mathsf{M}$ and the
weight-completed theorem.}
The chain-level class-$\mathsf{M}$ statement does not hold
at the direct-sum level: at generic central charge,
$S_4(\mathrm{Vir}_c)=10/[c(5c+22)]\ne 0$ forces bar cohomology
at weight~$4$, so strict chain-level quasi-isomorphism cannot
hold. This is the correct scope, not a gap. The correct
chain-level closure is in the \emph{weight-completed} category
via the strong filtration~$F^n=\bigoplus_{k\le n} B_k$, established as
\verb|thm:completed-bar-cobar-strong| in
Vol~I~\verb|chapters/theory/theorem_B_scope_platonic.tex|. The
harmonic discrepancy at each weight stage~$N$ is a finite sum
absorbed by an explicit chain homotopy $h\cdot m_0^{j-1}$; the
Milnor/Mittag-Leffler passage to inverse limit converges.

\textbf{(B.3) Class~$\mathsf{G}$/class~$\mathsf{L}$ chain-level
explicit.}
Class~$\mathsf{G}$ Heisenberg chain-level inversion is
unconditional via explicit MacLane splitting~$\sigma_{\mathrm{Heis}}$
on~$\mathrm{Sym}(V_{[1]})$. Class~$\mathsf{L}$ affine Kac--Moody at
non-critical level chain-level inversion is unconditional via the
PBW filtration and $E_2$-collapse lifting.

\subsection*{(C) Theorem~C: ambients}

Nine refinements to Theorem~C are recorded in the Theorem~C
refinement chapter. The list is as
follows.

\textbf{(C.1)} The brace-dg-algebra-level identification
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)\cong
Z^{\mathrm{der}}_{\mathrm{ch}}(\cA^!)$
as $E_2$-algebras after Deligne--Tamarkin is recorded as the
derived-centre Koszul-equivalence conjecture. The $H^0$-level naive
centre recovery with the Koszul pairing is proved unconditionally by
the naive-centre Koszul-identification lemma.

\textbf{(C.2)} Perfectness on the standard landscape is a
conditional proposition in the fiber-finiteness hypothesis. It is
unconditional for the Heisenberg family and for affine Kac--Moody
at positive integer or boundary admissible level, via
Tsuchiya--Ueno--Yamada propagation of finite conformal blocks in
the first case and Arakawa $C_2$-cofiniteness in the second. For
affine Kac--Moody at generic non-critical $k$ outside these loci,
the boundary-stratum finiteness is recorded as the generic
Kac--Moody boundary-perfectness conjecture. For
class~$\mathsf{M}$ the boundary-stratum fiber-finiteness is
recorded as the class~\(\mathsf M\) boundary-perfectness conjecture.

\textbf{(C.3)} $C_1$ reflexivity on the Koszul locus is
unconditional for the class~\(\mathsf G\) and class~\(\mathsf L\)
loci, and is conditional on the class~\(\mathsf M\) or generic
Kac--Moody boundary-perfectness conjectures for the rest of the
standard landscape.

\textbf{(C.4)} There is no $+3$ shift contradiction at $g = 0$:
the Verdier pairing of degree $-(3g{-}3)$ belongs to the \(g\geq1\)
clause of quantum complementarity; at $g=0$
the involution is trivial, $Q_0(\cA^!) = 0$, and no Verdier pairing
is invoked.

\textbf{(C.5)} The $C_2$ hypotheses are pinned:
BV~package + Verdier + bar-chart lift only. Uniform-weight is
\emph{not} a $C_2$ hypothesis but belongs to the
scalar-complementarity corollary.

\textbf{(C.6)} $C_0$ is unconditional for the class~\(\mathsf G\) and
class~\(\mathsf L\) families; the extension to the class~\(\mathsf M\)
standard landscape is conditional on class~\(\mathsf M\)
boundary-perfectness.

\textbf{(C.7)} The MC5 strengthening closes
class-$\mathsf{M}$ $C_2\textup{(iii)}$ in the weight-completed
category.

\textbf{(C.8)} The explicit cross-channel correction at
$(W_3, g{=}2)$ is inscribed:
$\delta F_2^{\mathrm{cross}}(W_3)=(c+204)/(16c)$
in the explicit \(W_3\), genus-\(2\) correction proposition.

\textbf{(C.9)} The mapping-stack
$R\mathrm{Map}(\overline{\cM}_g,BG_\cA)$
Pantev--To\"en--Vaqui\'e--Vezzosi presentation
has two separate clauses. The
shifted-symplectic form on the mapping stack is constructed
independently of the eigenspace decomposition; the Lagrangian
complementarity clause forwards to
the quantum-complementarity theorem and remains
conjectural until an intrinsic derived-stack construction of the
Verdier anti-symplectic involution is given.

\subsection*{(D) Theorem~D: globalization mechanisms}

Part~(i), the genus-$1$ formula $\obs_1=\kappa\cdot\lambda_1$,
is unconditional.

\textbf{(D.1) Virtual-class globalization.}
Via $K$-theoretic filtration,
$\lambda_{-1}(E)$, and the top-degree Chern-character identity
$\mathrm{ch}_g(\lambda_{-1}(E))=c_g(E)$ (splitting principle).

\textbf{(D.2) Faltings citation retargeted.}
The Arakelov--Faltings identification used in Proof~A is retargeted
from the unpublished Faltings source to Arakelov~1974 plus
Faltings~1984~\S2 plus Soul\'e~1992~Ch.~III (fiberwise
Chern-curvature formula for the Hodge bundle in the Arakelov
metric).

\textbf{(D.3) BGS $c_1(\det E)\to c_g(E)$ bridge.}
Via the splitting principle combined with scalar-channel linearity:
Chern--Weil for a scalar-endomorphism-valued curvature reads off
the top Chern class with a \emph{linear} scalar coefficient, not
a multiplicative one.

\textbf{(D.4) Clutching compatibility.}
The clutching proposition uses the genus-$1$ base,
separating-clutching additivity, nonseparating-clutching
compatibility, and tautological-ring purity to identify the same
scalar obstruction class in the tautological socle. No division by
\(\kappa\) is used; when \(\kappa=0\) the scalar obstruction is the
zero class and satisfies the same boundary restrictions.

\textbf{(D.5) Derived-stack route.}
The factorization-homology plus PTVV shifted-symplectic route is a
derived-categorical compatibility check. It does not remove the
scalar-diagonal uniform-weight hypothesis from the proved statement
of Theorem~D(ii).

Consequently Theorem~D(ii) is proved on the scalar-diagonal
uniform-weight lane by the GRR and clutching arguments of
\S\ref{subsec:thmD-proof}.

\subsection*{(H) Theorem~H: Step~3 circularity rerouted}

\textbf{(H.1) PBW Koszulity criterion.}
The circularity risk at Step~3 of the $\{0,1,2\}$ concentration
proof has been rerouted through
\verb|thm:pbw-koszulness-criterion| directly, via the
Shelton--Yuzvinsky Koszulity of braid-arrangement
Orlik--Solomon algebras plus the chiral quadratic-Koszul lemma.
Bar-concentration and FM-tower collapse are \emph{parallel
consequences} of the PBW collapse criterion, not sequential
inputs.

\textbf{(H.2) Independent verification paths.}
Three disjoint-source verification paths are stated for
Theorem~H: Heisenberg via Feigin--Frenkel CE (disjoint from
bar); Virasoro via Wang BRST and Feigin--Fuks (disjoint);
affine~$\mathfrak{sl}_2$ via Whitehead~+~K\"unneth (disjoint).

\textbf{(H.3) $E_1$-variant provable.}
The $E_1$ variant~\verb|thm:hochschild-concentration-E1| (for
Yangian input) is provable via $\mathrm{FM}^{\mathrm{ord}}$ plus
pure-braid Orlik--Solomon plus the ordered Koszul dual; the
symmetric-bar obstruction $R(z)\ne\tau$ is the quantum-group content.
The alternative H05 is retrievable as the sharp-Hilbert-series
statement from the \verb|fm-tower-collapse| $E_2$~page.

\subsection*{Structural adjacents}

\textbf{(E1) Iterated-Sugawara tower and topologization
(Vol~II).}
\verb|thm:iterated-sugawara-construction| and
\verb|thm:e-infinity-topologization-ladder| (Vol~II
\verb|chapters/connections/e_infinity_topologization.tex|)
promote the Sugawara construction of a single stress tensor to an
infinite tower of inner higher-spin Casimir tensors, each of which
raises the topologization level by one: $k$~inner stress tensors
yield $E_{k+2}^{\mathrm{top}}$. Virasoro at non-critical level
gives $E_3^{\mathrm{top}}$; finite $\cW_N$ gives
$E_{N+1}^{\mathrm{top}}$. The $\cW_\infty$ endpoint requires the
separate inverse-limit and completion hypotheses stated in Vol~II.

\textbf{(E2) Chiral higher Deligne (Vol~II).}
\verb|thm:chiral-higher-deligne| (Vol~II
\verb|chapters/theory/chiral_higher_deligne.tex|) identifies
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ as the universal
$E_3$-chiral algebra acted on by~$\mathrm{SC}^{\mathrm{ch,top}}$
via heptagon edges $(3)\leftrightarrow(4)\leftrightarrow(5)$.
This supplies a conditional second route to Theorem~H once the
chiral \(E_3\)-PBW theorem is established. The theorem proved in
this volume remains the ordered-bar/Orlik--Solomon concentration
statement.

\textbf{(E3) Periodic~CDG for admissible~KL (Vol~I).}
\verb|thm:periodic-cdg-is-koszul-compatible| (Vol~I
\verb|chapters/theory/periodic_cdg_admissible.tex|) closes
the admissible-level Kazhdan--Lusztig case: at
$k+h^\vee=p/q$, the periodic-CDG filtration
$F^n=\ker(Q^n_{\mathrm{adm}})$ on~$\mathrm{KL}_k^{\mathrm{adm}}$
is compatible with chiral Koszul duality; the chiral adjunction
$\Omega^{\mathrm{ch}}\dashv B^{\mathrm{ch}}$ descends
unconditionally.

\subsection*{Residual open frontiers}

The five theorems require the following scope conditions and open
obligations.

\textbf{(F.1) $\cW(p)$~triplet tempering.}
The Vol~II statement~\verb|thm:tempered-stratum-contains-wp|
is conjectural.
The Zhu-bounded-Massey proof chain fails: Gurarie~1993 and
Flohr~1996 construct logarithmic-CFT amplitudes with unbounded
Massey products despite finite-dimensional Zhu algebra. The
corrected tempered scope is: principal, non-logarithmic,
non-minimal standard landscape; $\cW(p)$ is open pending an
Adamovi\'c--Milas character-amplitude bound.

\textbf{(F.2) Non-tempered stratum.}
Emptiness of the non-tempered stratum in the $C_2$-cofinite
standard landscape holds on the non-logarithmic subset
(Virasoro, $\cW_N$, Schellekens, Monster, irrational cosets);
logarithmic $\cW(p)$ remains open.

\textbf{(F.3) Riccati-arithmetic primes.}
Primes $1423, 3067, 23, 43, 419$ have no primary-source
Bernoulli witness for Kummer irregularity. They still appear in
$S_r$~numerators as
Riccati-arithmetic characteristic primes rather than Kummer-arithmetic
primes. The Riccati emergence set is~$\{37, 691, 811\}$.

\textbf{(F.4) Super-Yangian complementarity.}
The super-Yangian complementarity sum splits by normalisation. The
super-trace form $\kappa^{\str}+\kappa^{\str,!}=0$ is proved for
$Y_\hbar(\mathfrak{sl}(m|n))$ on the sub-Sugawara line $m\neq n$ via
super-Sugawara rational-identity cancellation
(the Nazarov centrality and super-trace complementarity proposition).
The Berezinian form
$\kappa^{\sBer}+\kappa^{\sBer,!}=\max(m,n)$ at the Sugawara-shifted
dual level is conjectural, conditional
on a closed-form derivation of the $\tfrac{1}{2}\max(m,n)$ shift
magnitude induced by the central automorphism $\sigma_{\sBer}$.
Nazarov~1991 and Gow~2006 supply centrality of $\sBer(T(u))$ and
non-degeneracy of the Berezinian pairing, not the shift magnitude
in closed form; the identity is verified symbolically at small
rank as evidence, not derivation.

\textbf{(F.5) CY-C pentagon stratifies generator rank, not
$\kappa_{\mathrm{ch}}$ (Vol~III).}
The Vol~III pentagon of five intertwiners stratifies the
generator-lattice rank~$\rho^{R_i}\in\{3,12,24\}$, not the
chiral modular characteristic. $\kappa_{\mathrm{ch}}$ is
route-independent and equal to zero for K3$\times$E by the
Hodge supertrace. This is a CY-side correction with no effect on
the five theorems of Vol~I at their stated scopes.

\end{document}
