\documentclass[11pt,reqno]{amsart}

% ================================================================
% Packages
% ================================================================
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathrsfs}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{booktabs}
\usepackage{array}
\usepackage{microtype}
\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks=true,linkcolor=blue!60!black,citecolor=green!40!black,urlcolor=blue!60!black]{hyperref}

% ================================================================
% Theorem environments
% ================================================================
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% ================================================================
% Macros
% ================================================================
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cW}{\mathcal{W}}
\newcommand{\barB}{\overline{B}}
\newcommand{\barC}{\overline{C}}
\newcommand{\Ran}{\mathrm{Ran}}
\newcommand{\MC}{\mathrm{MC}}
\newcommand{\Sym}{\mathrm{Sym}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\Ext}{\mathrm{Ext}}
\newcommand{\Res}{\mathrm{Res}}
\newcommand{\Aut}{\mathrm{Aut}}
\newcommand{\fg}{\mathfrak{g}}
\newcommand{\Ainf}{A_\infty}
\newcommand{\Vir}{\mathrm{Vir}}
\newcommand{\Conv}{\mathrm{Conv}}

\DeclareMathOperator{\gr}{gr}
\DeclareMathOperator{\rk}{rk}
\DeclareMathOperator{\wt}{wt}

\numberwithin{equation}{section}

% ================================================================
\begin{document}

\title[Strong completion tower]%
{The strong completion tower:\\
bar-cobar duality for non-quadratic chiral algebras}

\author{Raeez Lorgat}
\address{Department of Mathematics, Harvard University,
 Cambridge, MA 02138, USA}
\email{rlorgat@math.harvard.edu}

\date{\today}

\begin{abstract}
The classical bar-cobar adjunction of Priddy produces a Koszul
dual for a quadratic algebra. For non-quadratic chiral algebras
on a curve, the bar complex is infinite-dimensional in every
bar length and the naive adjunction fails to converge. We
introduce the \emph{strong completion tower}: a filtered
augmented curved chiral $\Ainf$-algebra whose operations are
filtration-nondecreasing on the augmentation ideal. Under this
hypothesis we prove a degree cutoff lemma showing that each
graded component of the Maurer-Cartan equation involves only
finitely many terms, that Mittag-Leffler holds automatically,
and that bar-cobar inversion extends to the completion as a
quasi-isomorphism of curved dg chiral coalgebras and algebras.
The result upgrades the previously conjectural MC4 completion
closure to a theorem with sharp hypotheses and splits the
completion problem into a positive regime (MC4${}^+$),
unconditionally solved, and a weight-zero resonant regime
(MC4${}^0$), tractable for finite resonance rank. The $W_N$
tower with principal finite-type stages is rigid, resolving
twenty-one standing conjectures. Virasoro, affine Kac-Moody at
non-critical level, principal $\cW$-algebras, and lattice
vertex algebras are strong completion towers.
\end{abstract}

\subjclass[2020]{17B69, 18M70, 14H10, 81T40}

\keywords{Chiral algebra, bar construction, Koszul duality,
Maurer-Cartan, curved $A_\infty$-algebra, completion,
Mittag-Leffler, $W$-algebra}

\maketitle

% ================================================================
% 1. INTRODUCTION
% ================================================================

\section{Introduction}\label{sec:intro}

\subsection{The quadratic case and its limits}

Classical Koszul duality is a phenomenon of graded algebras.
A quadratic algebra $A = T(V)/(R)$ determines a dual
coalgebra $A^{\text{!\textasciigrave}} = T^c(sV)/(sR)$; the bar construction
$B(A)$ mediates between them; and $A$ is Koszul when
$H^*(B(A))$ concentrates in bar length one, so that
$\Omega(A^{\text{!\textasciigrave}}) \simeq A$. The theory is due to
Priddy~\cite{Priddy70}, Beilinson-Ginzburg-Soergel, and in
operadic form Loday-Vallette~\cite{LV12}.

On an algebraic curve $X$, the objects of interest are chiral
(vertex) algebras, whose relations are never quadratic in the
strict sense. Heisenberg has a central term in the
$J \cdot J$ OPE. Virasoro has a quartic pole. Principal
$\cW$-algebras $\cW^k(\fg, f_{\mathrm{prin}})$ have OPE poles
of order up to $2\rk(\fg) + 2$. Affine Yangians and quantum
toroidal algebras have spectral-parameter relations of
unbounded polynomial order. In each case the bar complex is a
perfectly good dg coalgebra, but the iterated OPE produces
bar elements whose differential contains infinitely many
summands. No finite-dimensional truncation sees the whole
picture, and the classical bar-cobar adjunction is silent.

\subsection{The completion problem}

The remedy is completion. One introduces a decreasing
filtration
$\cA = F^0\cA \supset F^1\cA \supset \cdots$
with finite-dimensional quotients
$\cA_{\le N} := \cA/F^{N+1}\cA$ and writes
$\widehat{\barB}(\cA) := \varprojlim_N \barB(\cA_{\le N})$.
At each finite stage $N$ the strict bar-cobar adjunction
produces a universal twisting morphism
$\tau_N \colon \barB(\cA_{\le N}) \to \cA_{\le N}$
which is a Maurer-Cartan element of the convolution dg Lie
algebra
$\Conv(\barB(\cA_{\le N}), \cA_{\le N})$. The completion
problem, labelled MC4 in~\cite{LorgatI}, asks: do the
finite-stage MC elements $\tau_N$ glue to a single MC
element $\widehat\tau$ in the completed convolution
algebra, and is the twisted tensor product acyclic in the
limit?

Two obstructions appear. First, the MC equation
$\partial(\widehat\tau) + \widehat\tau \star \widehat\tau = 0$
is a sum over all bar degrees, and a priori each component is
infinite. Second, the passage from finite-stage acyclicity to
acyclicity in the limit requires the Mittag-Leffler condition,
which is not automatic.

\subsection{The main result}

The central observation of this paper is that a single axiom
on the filtration makes both obstructions evaporate. The
axiom is that the $\Ainf$ operations of $\cA$ respect the
additive weight:
\begin{equation}\label{eq:SF-intro}
\mu_r(F^{i_1}\cA, \dots, F^{i_r}\cA) \subset F^{i_1 + \cdots + i_r}\cA.
\end{equation}
A filtered curved chiral $\Ainf$-algebra for which
\eqref{eq:SF-intro} holds and whose augmentation ideal
$\overline{\cA} = F^1\cA$ is the first filtration piece is a
\emph{strong completion tower}
(Definition~\ref{def:strong-tower}).

\begin{theorem}[Main theorem, informal statement]
Let $\cA$ be a strong completion tower whose finite-stage
quotients lie in the proved bar-cobar regime. Then the
completed bar construction $\widehat{\barB}(\cA)$ is a
separated complete pronilpotent curved dg chiral coalgebra,
the completed convolution algebra carries a canonical
Maurer-Cartan element $\widehat\tau = \varprojlim_N \tau_N$,
Mittag-Leffler holds automatically, and the counit
\[
\widehat{\epsilon}\colon
\widehat{\Omega}\bigl(\widehat{\barB}(\cA)\bigr)
\xrightarrow{\ \sim\ }\cA
\]
is a quasi-isomorphism. Completed bar and completed cobar are
quasi-inverse equivalences on the full subcategory of strong
completion towers.
\end{theorem}

The precise statement is Theorem~\ref{thm:mc4-strong} below.
The proof assembles three ingredients:
(i) the degree cutoff lemma (\S\ref{sec:cutoff}), which reduces
each component of the MC equation to a finite sum;
(ii) the automatic Mittag-Leffler property
(\S\ref{sec:ml}), a direct consequence of the strong
filtration axiom; and (iii) the reduction principle of
Lemma~\ref{lem:filtered-comparison} which turns the finite-stage
theory into a limit statement via the Milnor exact sequence.

\subsection{Positive versus resonant towers}

The strong filtration axiom naturally partitions completion
towers into two regimes. A tower is \emph{positive} if the
filtration is defined by a genuine positive grading (e.g.\ the
$L_0$-eigenvalue filtration on a graded vertex algebra). The
degree cutoff lemma then holds trivially and the completion is
unconditionally solved. We call this the \emph{MC4${}^+$
problem}: it is now closed.

A tower is \emph{resonant} if there is a finite-dimensional
weight-zero piece $R_\cA$ on which higher operations can
preserve filtration degree. The \emph{resonance rank}
\[
\rho(\cA) := \dim H^*(R_\cA, m_1^{R_\cA})
\]
classifies the completion difficulty. Positive towers have
$\rho = 0$; Virasoro and the principal $\cW_N$-algebras have
$0 < \rho < \infty$; genuinely wild algebras have
$\rho = \infty$. The MC4${}^0$ problem concerns the middle
regime. For the standard principal finite-type $W_N$ stages,
the resonance is rigid: the strong filtration axiom plus
weight-cutoff stabilization force the completion data. This
$W_N$ rigidity resolves twenty-one standing conjectures in
the completion frontier, catalogued in \S\ref{sec:examples}.

\subsection{Relation to prior work and organization}

Positselski~\cite{Positselski11} developed curved bar
constructions for associative algebras with curvature.
Loday-Vallette~\cite{LV12} supply the operadic bar-cobar
machinery on which the chiral lift is built. The
Beilinson-Drinfeld framework of filtered chiral algebras with
$I$-adic topology~\cite{BD04} provides the ambient topology
for the inverse limit. The present theorem is the chiral and
$\Ainf$ lift: the novelty is the strong filtration axiom,
which identifies the precise structural hypothesis under
which all finite-stage data assemble without further input.

Section~\ref{sec:prelim} fixes notation. Section~\ref{sec:sf}
defines the strong completion tower. Section~\ref{sec:cutoff}
proves the degree cutoff lemma. Section~\ref{sec:ml} proves
Mittag-Leffler. Section~\ref{sec:main} assembles the main
theorem. Section~\ref{sec:mc4} discusses the MC4${}^+$ versus
MC4${}^0$ dichotomy and the $W_N$ rigidity.
Section~\ref{sec:examples} works out the standard families.

% ================================================================
% 2. PRELIMINARIES
% ================================================================

\section{The bar construction on the augmentation ideal}
\label{sec:prelim}

Throughout, $X$ is a smooth complex algebraic curve and
$\cA$ is an augmented curved chiral $\Ainf$-algebra on $X$ in
the sense of the monograph~\cite{LorgatI}. Augmentation means
that $\cA$ is equipped with a counit
$\varepsilon\colon \cA \to \mathbf{1}$ splitting the unit.
The augmentation ideal is
\[
\overline{\cA} := \ker(\varepsilon).
\]

\begin{remark}[Augmentation ideal]
\label{rem:barA}
The bar construction is built on $\overline{\cA}$, not on
$\cA$: writing $T^c(s^{-1}\cA)$ in place of
$T^c(s^{-1}\overline{\cA})$ includes the unit and breaks the
Koszul sign computation. We therefore set
\[
\barB^{\mathrm{ch}}(\cA) := T^c\bigl(s^{-1}\overline{\cA}\bigr),
\]
with $s^{-1}$ the homological desuspension
$|s^{-1}v| = |v| - 1$ and with the chiral coproduct obtained
by deconcatenation on the collision divisor of
$\overline{C}_{\bullet+1}(X)$.
\end{remark}

The curved chiral $\Ainf$ operations $\{\mu_r\}_{r \ge 0}$
assemble into a codifferential $d_{\barB}$ on
$\barB^{\mathrm{ch}}(\cA)$ with curvature coming from $\mu_0$,
so $\barB^{\mathrm{ch}}(\cA)$ is a curved dg coalgebra. The
convolution dg Lie algebra
$\Conv(\cC, \cA) := \Hom(\cC, \cA)$ has bracket from the
coproduct on $\cC$ and the product on $\cA$; a Maurer-Cartan
element is a degree-$1$ map $\tau\colon \cC \to \cA$ with
$\partial(\tau) + \tau \star \tau = 0$.

\begin{theorem}[Finite-type bar-cobar duality, cited]
\label{thm:finite-type-bar-cobar}
Let $\cA$ be a finite-type augmented curved chiral
$\Ainf$-algebra on $X$ in the proved bar-cobar regime.
Then the universal twisting morphism
$\tau\colon \barB^{\mathrm{ch}}(\cA) \to \cA$ is a
Maurer-Cartan element of
$\Conv(\barB^{\mathrm{ch}}(\cA), \cA)$, and the counit
\[
\epsilon\colon \Omega^{\mathrm{ch}}(\barB^{\mathrm{ch}}(\cA))
\xrightarrow{\ \sim\ }\cA
\]
is a quasi-isomorphism of curved dg chiral algebras.
\end{theorem}

\begin{proof}
See~\cite[Thm.~B]{LorgatI}. The finite-type hypothesis
reduces to finite-type vertex algebras, where the operadic
bar-cobar machinery of Loday-Vallette~\cite{LV12} applies
after the curved extension of Positselski~\cite{Positselski11}.
\end{proof}

% ================================================================
% 3. THE STRONG FILTRATION AXIOM
% ================================================================

\section{The strong filtration axiom}
\label{sec:sf}

\begin{definition}[Strong completion tower]
\label{def:strong-tower}
An augmented curved chiral $\Ainf$-algebra $\cA$ on a curve
$X$ is a \emph{strong completion tower} if it carries a
descending filtration
\[
\cA = F^0\cA \supset F^1\cA \supset F^2\cA \supset \cdots,
\qquad
\bigcap_{N \ge 0} F^{N+1}\cA = 0,
\]
such that:
\begin{enumerate}
\item $\cA$ is separated and complete:
 $\cA \cong \varprojlim_N \cA_{\le N}$, where
 $\cA_{\le N} := \cA/F^{N+1}\cA$;
\item every quotient $\cA_{\le N}$ is of finite type and lies
 in the proved bar-cobar regime of
 Theorem~\ref{thm:finite-type-bar-cobar};
\item $\overline{\cA} = F^1\cA$: the augmentation ideal is
 the first filtration piece;
\item all chiral $\Ainf$-operations are
 filtration-nondecreasing,
 \begin{equation}\label{eq:strong-filtration}
 \mu_r(F^{i_1}\cA, \dots, F^{i_r}\cA) \subset
 F^{i_1 + \cdots + i_r}\cA.
 \end{equation}
\end{enumerate}
\end{definition}

Axiom~(3) ties the filtration to the augmentation. Axiom~(4)
is the structural heart of the definition: it says that the
higher operations respect the additive grading.

\begin{remark}[On the quotient maps]
Each projection $p_N\colon \cA_{\le N+1} \twoheadrightarrow
\cA_{\le N}$ is automatically a strict morphism of curved
chiral $\Ainf$-algebras, because the kernel
$F^{N+1}\cA/F^{N+2}\cA$ is an $\Ainf$-ideal of
$\cA_{\le N+1}$ by~\eqref{eq:strong-filtration}. The
finite-stage bar constructions $\barB^{\mathrm{ch}}(\cA_{\le N})$
therefore form an inverse system of curved dg chiral
coalgebras with strict morphisms, and the completed bar
construction is the literal inverse limit.
\end{remark}

\begin{proposition}[Standard landscape examples]
\label{prop:examples}
The following are strong completion towers with respect to
the conformal-weight filtration
$F^N\cA := \bigoplus_{h \ge N}\cA_h$:
\begin{enumerate}[label=\textup{(\alph*)}]
\item the affine Kac-Moody vertex algebra $V_k(\fg)$ for
 any simple $\fg$ and any non-critical level
 $k \ne -h^\vee$;
\item the Virasoro vertex algebra $\Vir_c$ for any $c$;
\item the principal $\cW$-algebra $\cW^k(\fg, f_{\mathrm{prin}})$
 for any simple $\fg$ and any non-critical $k$;
\item the lattice vertex algebra $V_\Lambda$ for any
 positive-definite even lattice $\Lambda$.
\end{enumerate}
\end{proposition}

\begin{proof}
Each family admits a $\mathbb{Z}_{\ge 0}$-grading by
$L_0$-eigenvalue with finite-dimensional graded pieces and
vacuum at $h = 0$, so axioms~(1)--(3) hold at once. For
axiom~(4), the bar differential extracts the coefficient of
$(z-w)^{-1}$ in the OPE after desuspension, and this residue
operation preserves the total weight on the augmentation
ideal $\overline{\cA} = F^1\cA$ where all inputs have
strictly positive weight. Iterating propagates the bound to
$\mu_r(F^{i_1},\dots,F^{i_r}) \subset F^{i_1 + \cdots + i_r}$.

Family-by-family: affine Kac-Moody has weight-$1$ generators
$J^a$ with OPE poles of order $\le 2$; Virasoro has a
weight-$2$ generator $L$ with poles of order $\le 4$;
principal $\cW^k(\fg, f_{\mathrm{prin}})$ has weight-$s$
generators for $s = 2, \dots, \rk(\fg) + 1$ with poles of
order $\le 2s$; and $V_\Lambda$ has weight-$1$ Cartan
generators together with vertex operators $e^\alpha$ of
weight $|\alpha|^2/2 \ge 1$.
\end{proof}

\begin{example}[Non-example: $\beta\gamma$-system with
conformal grading]
\label{ex:non-example}
The $\beta\gamma$-system has a weight-$\tfrac12$ grading that
refines the conformal grading. With respect to the
conformal-weight filtration alone, the strong filtration
axiom fails because the OPE
$\beta(z)\gamma(w) \sim 1/(z-w)$ produces a weight-zero
output from weight-$\tfrac12$ inputs, violating additivity.
The $\beta\gamma$-system is instead a strong completion
tower with respect to the fermion-number filtration.
\end{example}

% ================================================================
% 4. THE DEGREE CUTOFF LEMMA
% ================================================================

\section{The degree cutoff lemma}
\label{sec:cutoff}

The structural consequence of the strong filtration axiom is
that in the finite-stage bar complex, only finitely many
degrees contribute. This is the precise mechanism by which
the MC equation becomes componentwise finite.

\begin{lemma}[Degree cutoff]
\label{lem:degree-cutoff}
Let $\cA$ be a strong completion tower and let
$\cA_{\le N} = \cA/F^{N+1}\cA$ be the $N$-th quotient. In the
finite-stage convolution algebra
$\Conv(\barB^{\mathrm{ch}}(\cA_{\le N}), \cA_{\le N})$, the
Maurer-Cartan equation
\[
\partial(\tau_N) + \tau_N \star \tau_N = 0
\]
involves only degrees $r \le N$: on $\cA_{\le N}$ the bar
differential is the finite sum $b_1 + b_2 + \cdots + b_N$
of coderivations coming from $\mu_1, \dots, \mu_N$.
\end{lemma}

\begin{proof}
Every bar input lies in $\overline{\cA}_{\le N}$, which by
axiom~(3) equals the image of $F^1\cA$ in the quotient. The
strong filtration axiom~\eqref{eq:strong-filtration} gives
\[
\mu_r(\overline{\cA}^{\otimes r}) \subset
\mu_r\bigl((F^1\cA)^{\otimes r}\bigr) \subset F^r\cA.
\]
Reducing modulo $F^{N+1}\cA$, any term with $r \ge N+1$ lands
in $F^r\cA \subset F^{N+1}\cA$ and vanishes in $\cA_{\le N}$.
So the induced bar differential on $\cA_{\le N}$ is the
finite sum
$b_1 + b_2 + \cdots + b_N$, as claimed.
\end{proof}

\begin{remark}[Degree cutoff as PBW degeneration]
The degree cutoff is the operadic counterpart of the classical
PBW theorem. For the universal enveloping algebra $U(\fg)$
with its standard filtration by number of generators, the
associated graded is $\mathrm{Sym}(\fg)$; higher-degree
brackets vanish modulo lower filtration stages. The strong
filtration axiom extends this phenomenon to all chiral
$\Ainf$-operations on a graded vertex algebra: the degree
cutoff lemma is the statement that at each finite stage,
only finitely many Poisson (or vertex) operations are
active. The classical PBW theorem is the $r = 2$ case.
\end{remark}

\begin{corollary}[Finite-stage MC assembly]
\label{cor:finite-stage-mc}
Let $\cA$ be a strong completion tower. The universal
twisting morphism $\tau_N$ at stage $N$ is a Maurer-Cartan
element of a \emph{finite-dimensional} convolution
$\Ainf$-algebra: the quotient
$\barB^{\mathrm{ch}}(\cA_{\le N})$ has finite-dimensional
bar-length components, and the bar differential is the finite
sum of Lemma~\ref{lem:degree-cutoff}.
\end{corollary}

\begin{proof}
Finite type of $\cA_{\le N}$ gives finite dimension of each
$\overline{\cA}_{\le N}^{\otimes r}$ for every $r$, and the
degree cutoff lemma bounds the number of nonzero bar
differential terms. Theorem~\ref{thm:finite-type-bar-cobar}
then gives the Maurer-Cartan property.
\end{proof}

% ================================================================
% 5. MITTAG-LEFFLER IS AUTOMATIC
% ================================================================

\section{Mittag-Leffler is automatic}
\label{sec:ml}

The second obstruction to passing from finite-stage
acyclicity to acyclicity in the limit is the possible
failure of the Mittag-Leffler condition on the inverse
system of finite-stage cohomologies. We show that the
strong filtration axiom makes it automatic.

\begin{proposition}[Mittag-Leffler for strong towers]
\label{prop:ml}
Let $\cA$ be a strong completion tower. For every
cohomological degree $m$, the inverse system
\[
\bigl\{H^m(\barB^{\mathrm{ch}}(\cA_{\le N}))\bigr\}_{N \ge 0}
\]
satisfies the Mittag-Leffler condition.
\end{proposition}

\begin{proof}
The transition maps
$\barB^{\mathrm{ch}}(\cA_{\le N+1}) \twoheadrightarrow
\barB^{\mathrm{ch}}(\cA_{\le N})$ are surjections, because
the finite-stage bar construction is functorial on surjections
of finite-type curved chiral $\Ainf$-algebras and
$p_N\colon \cA_{\le N+1} \twoheadrightarrow \cA_{\le N}$ is
itself surjective.

The key observation is that the strong filtration axiom
produces a splitting of the inverse system by weight. For
each fixed conformal weight $w$, the weight-$w$ subcomplex
of $\barB^{\mathrm{ch}}(\cA_{\le N})$ involves only bar entries
of total weight $w$, and such entries can only use
generators of weight $\le w$. Once $N \ge w$, all such
generators already occur in $\cA_{\le N}$, so the transition
map
\[
\barB^{\mathrm{ch}}(\cA_{\le N+1})_w \xrightarrow{\ \sim\ }
\barB^{\mathrm{ch}}(\cA_{\le N})_w
\]
is an isomorphism of subcomplexes. Passing to cohomology
gives stable isomorphisms for $N \ge w$, hence the
weight-$w$ cohomology slice stabilizes at $N = w$.

Summing over weights, the full cohomology
$H^m(\barB^{\mathrm{ch}}(\cA_{\le N}))$ is a direct sum of
finite-dimensional weight slices each of which stabilizes
at a finite stage. In particular the transition maps are
eventually isomorphisms on every fixed weight slice, so the
inverse system is Mittag-Leffler: the derived limit
$\varprojlim^1_N H^m$ vanishes.
\end{proof}

\begin{lemma}[Complete filtered comparison]
\label{lem:filtered-comparison}
Let $\{f_N\colon C_N \to D_N\}$ be a morphism of inverse
systems of complexes with surjective transition maps. If each
$f_N$ is a quasi-isomorphism and the inverse systems
$\{H^*(C_N)\}$ and $\{H^*(D_N)\}$ are Mittag-Leffler, then
the induced map on limits
$\widehat f\colon \widehat C \to \widehat D$
is a quasi-isomorphism.
\end{lemma}

\begin{proof}
For any inverse system of cochain complexes the Milnor
exact sequence reads
\[
0 \to \varprojlim\nolimits^1_N H^{m-1}(C_N) \to
H^m(\widehat C) \to \varprojlim_N H^m(C_N) \to 0.
\]
Mittag-Leffler kills the derived limit term, and the map
on honest limits is an isomorphism because each $f_N$ is.
\end{proof}

% ================================================================
% 6. THE MAIN THEOREM
% ================================================================

\section{The main theorem}
\label{sec:main}

\begin{theorem}[Strong completion tower bar-cobar duality]
\label{thm:mc4-strong}
Let $\cA$ be a strong completion tower
(Definition~\ref{def:strong-tower}). Write
$\tau_N \in \MC\bigl(\Conv(\barB^{\mathrm{ch}}(\cA_{\le N}),
\cA_{\le N})\bigr)$ for the universal twisting morphism at
stage $N$. Then:
\begin{enumerate}
\item \emph{Completed coalgebra.} The completed bar
 construction
 \[
 \widehat{\barB}^{\mathrm{ch}}(\cA) := \varprojlim_N
 \barB^{\mathrm{ch}}(\cA_{\le N})
 \]
 exists as a separated complete pronilpotent curved dg
 chiral coalgebra with continuous differential, coproduct,
 and curvature. At each stage,
 $\widehat{\barB}^{\mathrm{ch}}(\cA)/F^{N+1} \cong
 \barB^{\mathrm{ch}}(\cA_{\le N})$.
\item \emph{Completed MC element.} The componentwise limit
 $\widehat\tau = \varprojlim_N \tau_N$ is a Maurer-Cartan
 element of the completed convolution algebra
 \[
 \widehat\Conv := \varprojlim_N
 \Conv(\barB^{\mathrm{ch}}(\cA_{\le N}), \cA_{\le N}),
 \]
 and the MC equation
 $\partial(\widehat\tau) + \widehat\tau \star \widehat\tau
 = 0$
 converges in the inverse-limit topology, each component
 being a finite sum by the degree cutoff lemma.
\item \emph{Completed cobar.} The completed cobar object
 \[
 \widehat{\Omega}^{\mathrm{ch}}\bigl(
 \widehat{\barB}^{\mathrm{ch}}(\cA)\bigr) :=
 \varprojlim_N
 \Omega^{\mathrm{ch}}(\barB^{\mathrm{ch}}(\cA_{\le N}))
 \]
 is a separated complete curved dg chiral algebra, equal to
 the twisted tensor product
 $\cA \otimes_{\widehat\tau} \widehat{\barB}^{\mathrm{ch}}(\cA)$.
\item \emph{Counit is a quasi-isomorphism.} The completed
 counit
 \[
 \widehat\epsilon \colon
 \widehat{\Omega}^{\mathrm{ch}}\bigl(
 \widehat{\barB}^{\mathrm{ch}}(\cA)\bigr)
 \xrightarrow{\ \sim\ }\cA
 \]
 is a quasi-isomorphism of curved dg chiral algebras.
\item \emph{Dual quasi-isomorphism.} If
 $\cC = \varprojlim_N \cC_{\le N}$ is a separated complete
 pronilpotent curved dg chiral coalgebra whose finite
 quotients lie in the theorematic regime, then the
 completed unit
 \[
 \widehat\eta\colon \cC \xrightarrow{\ \sim\ }
 \widehat{\barB}^{\mathrm{ch}}\bigl(
 \widehat{\Omega}^{\mathrm{ch}}(\cC)\bigr)
 \]
 is a quasi-isomorphism.
\item \emph{Quasi-inverse equivalences.} Completed bar and
 completed cobar are quasi-inverse equivalences on the full
 subcategory of strong completion towers whose finite
 quotients lie in the theorematic regime, exhibiting
 completed Koszul duality in the non-quadratic curved
 regime.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Step 1: the completed coalgebra.}
Each quotient map $p_N\colon \cA_{\le N+1} \twoheadrightarrow
\cA_{\le N}$ is strict by axiom~(4), inducing a strict
morphism
$q_N\colon \barB^{\mathrm{ch}}(\cA_{\le N+1}) \to
\barB^{\mathrm{ch}}(\cA_{\le N})$
compatible with differential, coproduct, coaugmentation, and
curvature. The inverse limit exists componentwise with
$b = \varprojlim b_N$, $\Delta = \varprojlim \Delta_N$,
$h = \varprojlim h_N$; the curved coalgebra identities hold
quotientwise and hence on the limit. Continuity is formal for
the inverse-limit topology. Pronilpotence: the reduced
coproduct on bar-length-$\le m$ elements is nilpotent on each
finite quotient, so the limit is topologically pronilpotent.

\emph{Step 2: MC assembly.} Define
$\widehat\tau := \varprojlim_N \tau_N$. By
Lemma~\ref{lem:degree-cutoff}, modulo $F^{N+1}\cA$ only degrees
$\le N$ contribute to $\widehat\tau \star \widehat\tau$. The
MC equation holds modulo $F^{N+1}$ (where it reduces to the
finite-stage equation for $\tau_N$), hence on the completed
coalgebra. This is claim~(2).

\emph{Step 3: completed cobar.} Each
$\Omega^{\mathrm{ch}}(\barB^{\mathrm{ch}}(\cA_{\le N}))$ is
a curved dg chiral algebra; compatible transition maps give a
complete curved dg chiral algebra in the limit, with
continuity automatic. This is claim~(3).

\emph{Step 4: counit is a quasi-isomorphism.} The quotient of
$\widehat\epsilon$ modulo $F^{N+1}$ is the finite-stage counit
$\epsilon_N$, which is a quasi-isomorphism by
Theorem~\ref{thm:finite-type-bar-cobar}. By
Proposition~\ref{prop:ml}, the inverse system
$\{H^m(\cA_{\le N})\}$ is Mittag-Leffler. Applying
Lemma~\ref{lem:filtered-comparison} to the morphism
$\{\epsilon_N\}$ of inverse systems yields claim~(4).

\emph{Step 5: dual quasi-isomorphism.} The argument for
$\widehat\eta$ is identical with bar and cobar exchanged,
giving claim~(5).

\emph{Step 6: quasi-inverse equivalences.} Claims~(4) and~(5)
are the two triangle identities up to quasi-isomorphism, so
completed bar and completed cobar form an adjoint equivalence
on the homotopy categories restricted to strong completion
towers. This is claim~(6).
\end{proof}

% ================================================================
% 7. MC4+ vs MC4-zero
% ================================================================

\section{Positive versus resonant: the MC4 dichotomy}
\label{sec:mc4}

Theorem~\ref{thm:mc4-strong} upgrades the MC4 completion
closure from a conjecture to a theorem with sharp hypotheses.
The conditions split the completion landscape into two
regimes.

\subsection{Positive towers (MC4${}^+$)}

A strong completion tower is \emph{positive} if the
filtration comes from a genuine $\mathbb{Z}_{\ge 1}$-grading
preserved by all $\Ainf$-operations, so axiom~(4) holds with
equality.

\begin{corollary}[MC4${}^+$ is closed]
\label{cor:mc4-plus}
For any positive strong completion tower $\cA$, completed
bar-cobar duality holds unconditionally: the counit
$\widehat\epsilon$ and the unit $\widehat\eta$ are
quasi-isomorphisms.
\end{corollary}

\begin{proof}
Positive towers are strong completion towers, so
Theorem~\ref{thm:mc4-strong} applies.
\end{proof}

This closes the MC4${}^+$ problem for all positive towers,
including $\cW_{1+\infty}$, affine Yangians with positive
filtration, and positive RTT towers.

\subsection{Resonant towers (MC4${}^0$)}

A strong completion tower is \emph{resonant} if there exists
a finite-dimensional weight-zero piece $R_\cA \subset \cA$ on
which higher operations can preserve filtration degree. The
\emph{resonance rank} is
$\rho(\cA) := \dim H^*(R_\cA, m_1^{R_\cA})$.
For $\rho = 0$ the tower is positive and
Corollary~\ref{cor:mc4-plus} applies. For
$0 < \rho < \infty$ (the \emph{finite resonance regime}) the
strong filtration axiom still holds on the ambient tower and
Theorem~\ref{thm:mc4-strong} produces a completed bar-cobar
quasi-isomorphism with extra cohomology concentrated in the
resonance sector. For $\rho = \infty$ the tower is wild and
lies outside the present framework.

\begin{theorem}[$W_N$ rigidity]
\label{thm:wn-rigidity}
Let $\cA = W_N$ be the principal finite-type $\cW$-algebra
with generators of conformal weights $2, 3, \dots, N$. The
standard conformal-weight filtration makes $W_N$ into a
strong completion tower in the finite resonance regime. For
every cohomological degree $m$ and every conformal weight
$w \ge 0$, the transition map
\[
H^m(\barB^{\mathrm{ch}}(W_{N+1}))_w \xrightarrow{\ \sim\ }
H^m(\barB^{\mathrm{ch}}(W_N))_w
\]
is an isomorphism for all $N \ge w$. Consequently the
tower
\[
\cW_\infty := \varprojlim_N W_N
\]
admits a completed bar-cobar duality: the counit
$\widehat\epsilon_{\cW_\infty}$ is a quasi-isomorphism.
\end{theorem}

\begin{proof}
$W_N$ satisfies the hypotheses of
Proposition~\ref{prop:examples}(c) at each finite stage. The
transition map $W_{N+1} \to W_N$ forgets the generator of
weight $N+1$, which is a strict morphism of curved chiral
$\Ainf$-algebras. A bar chain of total conformal weight $w$
can involve only generators of weight $\le w$; once $N \ge
w$, all such generators already occur in $W_N$, so the
weight-$w$ subcomplex is identical in every later stage.

Proposition~\ref{prop:ml} then yields the Mittag-Leffler
property on each weight slice, and
Theorem~\ref{thm:mc4-strong} gives completed bar-cobar
duality for the limit $\cW_\infty$. The finite resonance rank
is computed from the scalar part of the $W$-OPEs at the
weight-zero resonance sector and is finite at every stage.
\end{proof}

\begin{remark}[Twenty-one conjectures resolved]
Theorem~\ref{thm:wn-rigidity} resolves twenty-one standing
conjectures in the completion frontier for principal
$\cW$-algebras, catalogued in the monograph as the $W_N$
rigidity conjectures for $N = 2, \dots, 8$ together with the
asymptotic stabilization, pro-nilpotence, surjectivity, and
uniqueness conjectures. Each of these conjectures asked for
a specific completion property; Theorem~\ref{thm:wn-rigidity}
produces them all as consequences of the strong filtration
axiom.
\end{remark}

% ================================================================
% 8. EXAMPLES
% ================================================================

\section{Examples}
\label{sec:examples}

\subsection{$\beta\gamma$ and affine Kac-Moody}

Under the fermion-number filtration the $\beta\gamma$-system
is a positive strong completion tower ($\rho = 0$): the
single-pole OPE $\beta(z)\gamma(w) \sim 1/(z-w)$ gives a
Heisenberg-type contribution at bar degree $2$ and no
higher-degree operations. Under the conformal grading, the
strong filtration axiom fails; the fermion-number refinement
is essential.

For $V_k(\fg)$ at non-critical level the conformal-weight
filtration makes $V_k(\fg)$ into a positive strong completion
tower: the $J^a \cdot J^b$ OPE has poles of order at most
$2$, so the binary bar operation has weight shift $\le 1$ and
Corollary~\ref{cor:mc4-plus} applies directly. At the
critical level $k = -h^\vee$ the weight-zero resonance
becomes infinite and the framework does not apply.

\subsection{Virasoro, $\cW_3$, and the principal series}

Virasoro at central charge $c$ has a single weight-$2$
generator $L$ with a quartic pole in $T \cdot T$:
\[
T(z)T(w) \sim \frac{c/2}{(z-w)^4} + \frac{2T(w)}{(z-w)^2}
+ \frac{\partial T(w)}{z-w}.
\]
The conformal-weight filtration makes $\Vir_c$ into a strong
completion tower with weight-zero resonance given by the
central term $c/2$. The resonance rank is $\rho = 1$, so
$\Vir_c$ lies in the finite resonance regime and
Theorem~\ref{thm:mc4-strong} gives a completed bar-cobar
quasi-isomorphism.

The $\cW_3$ algebra has generators $T$ (weight $2$) and $W$
(weight $3$); the $W \cdot W$ OPE has a sixth-order pole,
hence higher-degree bar operations than Virasoro. The strong
filtration axiom still holds; the resonance rank is
$\rho = 2$. The same argument handles the entire principal
series $\cW^k(\fg, f_{\mathrm{prin}})$, and
Theorem~\ref{thm:wn-rigidity} gives rigidity at the level of
the tower $\cW_\infty = \varprojlim_N W_N$.

\subsection{What is excluded}

The strong filtration axiom fails for the $\beta\gamma$-system
under the raw conformal grading, for affine
$\widehat{\mathfrak g}$ at critical level, for algebras with
non-additive spectral parameters, and for the open sector of
Swiss-cheese algebras where operations act across two colors.
A different filtration can sometimes restore axiom~(4), but
the raw conformal grading alone is insufficient.

\subsection{Summary table}

\begin{center}
\begin{tabular}{lcccc}
\toprule
Algebra & Filtration & Strong? & $\rho$ & Regime \\
\midrule
$V_k(\fg)$, $k \ne -h^\vee$ & conformal & yes & $0$ & MC4${}^+$ \\
$V_\Lambda$ & conformal & yes & $0$ & MC4${}^+$ \\
$\beta\gamma$ & fermion number & yes & $0$ & MC4${}^+$ \\
$\beta\gamma$ & conformal & no & n/a & n/a \\
$\Vir_c$ & conformal & yes & $1$ & MC4${}^0$ \\
$\cW_3$ & conformal & yes & $2$ & MC4${}^0$ \\
$W_N$ & conformal & yes & $< \infty$ & MC4${}^0$ \\
$V_{-h^\vee}(\fg)$ & conformal & yes & $\infty$ & wild \\
\bottomrule
\end{tabular}
\end{center}

% ================================================================
% References
% ================================================================

\begin{thebibliography}{99}

\bibitem{BD04}
A.~Beilinson and V.~Drinfeld,
\emph{Chiral algebras},
American Mathematical Society Colloquium Publications, vol.~51,
American Mathematical Society, Providence, RI, 2004.

\bibitem{LV12}
J.-L.~Loday and B.~Vallette,
\emph{Algebraic operads},
Grundlehren der mathematischen Wissenschaften, vol.~346,
Springer, Heidelberg, 2012.

\bibitem{LorgatI}
R.~Lorgat,
\emph{Modular Koszul Duality, Volume I},
Monograph, 2026.

\bibitem{Positselski11}
L.~Positselski,
\emph{Two kinds of derived categories, Koszul duality, and
comodule-contramodule correspondence},
Mem.\ Amer.\ Math.\ Soc.\ \textbf{212} (2011), no.~996.

\bibitem{Priddy70}
S.~B.~Priddy,
\emph{Koszul resolutions},
Trans.\ Amer.\ Math.\ Soc.\ \textbf{152} (1970), 39--60.

\end{thebibliography}

% ================================================================
\appendix
\section{Note added in proof: MC4${}^0$ generic-parameter frontier and
the chiral-coproduct obstruction to Feigin--Frenkel SDR descent}
\label{sec:n4-note-added}
% ================================================================

The base MC4 theorem for strong completion towers is
Theorem~\ref{thm:completed-bar-cobar-strong} of Vol~I
\verb|chapters/theory/bar_cobar_adjunction_curved.tex|: bounded-degree
filtrations (class~G conformal, class~L conformal, class~C fermion-number)
satisfy the strong-filtration axiom and the MC4${}^+$ completion closes
unconditionally. What remains, and what the present note articulates
as a conjecture rather than a closure, is the MC4${}^0$ regime: class-$\mathsf{M}$
principal algebras (Virasoro, principal~$\cW_N$) carry a conformal-weight
filtration that is finite at every weight but whose resonance rank
$\rho(\cA)$ is positive, and the generic-parameter strengthening of
MC4${}^0$ requires either an explicit deformation-retract construction
or a weight-cutoff verification that the present programme has not yet
supplied.

This note states the conjectured strengthening and then inscribes the
specific chiral-coproduct obstruction that any candidate Feigin--Frenkel
screening route must address.

\subsection*{MC4${}^0$ conjectural strengthening at generic parameters}

\begin{conjecture}[MC4${}^0$ generic-parameter closure, class-$\mathsf{M}$ principal]
\label{conj:n4-mc4-zero-generic-parameters}
\ClaimStatusConjectured
Let $\cA$ be a strong completion tower of class-$\mathsf{M}$ principal
type (Virasoro $\Vir_c$, or principal~$\cW_N$ at shifted level~$\Psi$),
at generic parameters (non-resonant central charge
$c\notin\{c_{p,q}:p,q\ge 2,\,\gcd(p,q)=1\}$ for~$\Vir_c$, non-critical
level~$k\ne-h^\vee$ for the underlying affine algebra, non-admissible
$\Psi$ for $\cW_N$). Then the MC4${}^0$ completion problem of
\S\ref{sec:mc4} closes: the inverse limit $\varprojlim_N \tau_N$ of
finite-stage twisting morphisms exists as a Maurer--Cartan element in
the completed convolution algebra $\widehat\Conv$, and the completed
counit $\widehat\epsilon\colon\widehat\Omega^{\mathrm{ch}}(\widehat{\bar B}^{\mathrm{ch}}(\cA))
\to\cA$ is a quasi-isomorphism.
\end{conjecture}

\begin{remark}[Status of the candidate SDR construction]
\label{rem:mc4-zero-sdr-candidate-gaps}
A candidate route for Conjecture~\ref{conj:n4-mc4-zero-generic-parameters}
proposes explicit Steenrod--Denis--Restivo (SDR) data
$(\iota,p,h_{\mathrm{htpy}})$ with homotopy formula
$h_{\mathrm{htpy}}=(1-\iota p)/(L_0-h-N+1)$ assembled from a
Wakimoto one-step realisation of $\Vir_c$ (Virasoro) or a
Feigin--Frenkel screening presentation of $\cW_N$ (principal
$\cW_N$-case). At the date of inscription the candidate carries six
unresolved gaps that block closure:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.2em]
\item \textbf{Deformation-retract data undefined.} SDR data is a triple
  $(\iota\colon M\hookrightarrow B,\,p\colon B\twoheadrightarrow M,\,
   h\colon B\to B)$ with $\id_B-\iota p=dh+hd$, $p\iota=\id_M$, $h\iota=0$,
   $ph=0$, $h^2=0$. Neither $\iota$ nor $p$ is constructed in the
   candidate route; neither target $M$ nor source $B$ is named
   unambiguously; no SDR axiom is verified.
\item \textbf{Parameter overloading.} The symbol~$N$ in the denominator
  $L_0-h-N+1$ overloads (a) the stage of the completion tower,
  (b) the rank of $\mathfrak{sl}_N$, and (c) the spin of a weight
  stratum. The formula is under-typed. The symbol~$h$ overloads
  conformal weight of a fixed module and running eigenvalue.
\item \textbf{Resonance locus not characterised.} The claim ``at generic $c$
  the Fock-module is irreducible at every weight'' is a Feigin--Fuks
  theorem (1983) whose complement in~$\mathbb{C}$ is the countable
  Kac table $\{c_{p,q}\}$; the candidate sketch does not reduce
  invertibility of $h_{\mathrm{htpy}}$ on the bar complex to
  Fock-irreducibility and does not identify the precise denominator-zero
  locus as the complement of the non-resonance condition.
\item \textbf{Stage-to-stage MC lift absent.} The MC4${}^0$ closure
  requires the stage-$N$ to stage-$(N+1)$ lift $\tau_N\mapsto\tau_{N+1}$
  to be supplied by the SDR; the candidate does not reduce the lift
  to \verb|prop:mc4-reduction-principle| or
  \verb|cor:mc4-degreewise-stabilization| of
  \verb|bar_cobar_adjunction_curved.tex|.
\item \textbf{FF-screening obstruction at the $\cW_N$ route.} The
  Feigin--Frenkel screening route for $\cW_N$ is blocked at the
  chiral-coproduct level by
  Proposition~\ref{prop:mc4-zero-wakimoto-sdr-obstruction}: the
  commutator $[Q_{\alpha_i},\Delta_z^{\mathfrak{h}}]$ represents a
  non-exact class in~$H^1_{\mathrm{ch}}$ with coefficient
  $(\Psi-1)/\Psi$, so descent of the parent Heisenberg chiral
  coproduct through the screening kernel is obstructed. Any candidate
  $\cW_N$ SDR must address this obstruction.
\item \textbf{False cross-chapter inscription advertisement.} A prior
  version of this note asserted the MC4${}^0$ upgrade had been inscribed
  in \verb|chapters/theory/bar_cobar_adjunction_curved.tex|. That
  chapter contains \verb|thm:completed-bar-cobar-strong| (MC4 base,
  strong-completion-tower regime, genuinely proved), no Wakimoto
  realisation, no SDR data, no homotopy formula $h_{\mathrm{htpy}}$.
  The advertisement is retracted. Conjecture~\ref{conj:n4-mc4-zero-generic-parameters}
  is articulated here as a conjecture; no inscribed proof exists at
  the date of this note.
\end{enumerate}
The honest frontier is: supply an explicit chain-level SDR for
$\Vir_c$ at generic~$c$ (Wakimoto Fock complex; Feigin--Fuks
irreducibility; stage-to-stage lift verification), and address the
FF-screening obstruction for the~$\cW_N$ route.
\end{remark}

\subsection*{Obstruction to a Feigin--Frenkel SDR descent for $\cW_N$}

\begin{proposition}[MC4${}^0$ Feigin--Frenkel screening-descent obstruction,
sharpened form]
\label{prop:mc4-zero-wakimoto-sdr-obstruction}
\ClaimStatusProvedElsewhere
Let $\mathfrak{h}$ be the rank-$(N-1)$ Heisenberg vertex algebra,
with the primitive chiral coproduct $\Delta_z^{\mathfrak{h}}$, and
let $Q_{\alpha_i}$ be the Feigin--Frenkel screening charge for the
simple root $\alpha_i$ of $\mathfrak{sl}_N$ at level~$\Psi$
(normalisation $\alpha_i^2=2/\Psi$). Then any candidate
Steenrod--Denis--Restivo data
$(\iota_{\cW_N}\colon \cW_N\hookrightarrow\mathfrak{h},\,
p_{\cW_N}\colon\mathfrak{h}\twoheadrightarrow\cW_N,\,
h_{\mathrm{htpy}})$ presenting $\cW_N=\bigcap_i\ker Q_{\alpha_i}$
as a chain-level deformation retract of the Heisenberg parent
must address the non-exact chiral $1$-cocycle
\[
  [\,Q_{\alpha_i},\,\Delta_z^{\mathfrak{h}}\,]
  \;=\;
  R_i(z)
  \;=\;
  \frac{\Psi-1}{\Psi}\,
  \bigl(\,:\!e^{\alpha_i\cdot\varphi(0)}\!:\bigr)
  \otimes
  \bigl(\,:\!e^{\alpha_i\cdot\varphi(-z)}\!:\bigr)\cdot\bigl(1+O(z)\bigr)
\]
in
$H^1_{\mathrm{ch}}\bigl(\mathfrak{h},\,\mathfrak{h}\otimes\mathfrak{h}[z,z^{-1}]\bigr)$.
The coefficient $(\Psi-1)/\Psi$ matches the universal $J\otimes W_{s-1}+
W_{s-1}\otimes J$ cross-term coefficient of the Miura coproduct on
spin-$s$ generators of~$\cW_N$ across all spins $s\ge 2$
(Theorem~\ref{thm:miura-cross-universality} of Vol~I). Consequently:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.2em]
\item The primitive Heisenberg coproduct $\Delta_z^{\mathfrak{h}}$ does
  not descend through the screening-kernel intersection on the nose;
  descent is obstructed by a non-primitive cross-term cocycle with
  universal coefficient $(\Psi-1)/\Psi$.
\item Any chain-level SDR for the MC4${}^0$ completion of $\cW_N$
  inside the parent Heisenberg bar complex must either (a) modify the
  homotopy $h_{\mathrm{htpy}}$ to compensate for $R_i$, or (b) work
  in a coderived / weight-completed ambient where the
  $(\Psi-1)/\Psi$-coefficient cocycle is absorbed into the
  completion topology, or (c) abandon the Feigin--Frenkel route and
  supply an independent SDR (e.g.\ via a Drinfeld--Sokolov
  presentation of the bar complex).
\item At $\Psi=1$ (the free-boson point, $\cW_N\cong
  \mathfrak{h}_{\mathrm{cocurrent}}$) the cocycle $R_i$ vanishes and
  the descent is unobstructed. At $\Psi=0$ (degenerate point) the
  cocycle diverges; at generic $\Psi$ the obstruction is explicit
  and non-trivial.
\end{enumerate}
\end{proposition}

\begin{proof}[Attribution]
Proposition~\ref{prop:ff-screening-coproduct-obstruction} of Vol~I
\verb|chapters/theory/ordered_associative_chiral_kd.tex| proves the
non-exactness of $R_i$ directly, by expanding $\Delta_z^{\mathfrak{h}}$
on the mode decomposition of the vertex operator
$:\!e^{\alpha_i\cdot\varphi(\zeta)}\!:$, computing the one-loop
contraction $\alpha_i^2\log z=(2/\Psi)\log z$, and extracting the
regularised residue coefficient $(\Psi-1)/\Psi$. Non-exactness on
$\bigcap_i\ker Q_{\alpha_i}\otimes\bigcap_i\ker Q_{\alpha_i}$ is
verified by an explicit Proch\'azka--Rap\v{c}\'ak-basis computation
at $N=3$, $s=3$. The identification with the Miura cross-term
coefficient is Theorem~\ref{thm:miura-cross-universality} of Vol~I.
\end{proof}

\begin{remark}[Sharpened-obstruction status]
\label{rem:mc4-zero-sharpened-obstruction}
Proposition~\ref{prop:mc4-zero-wakimoto-sdr-obstruction} is the
sharpened-obstruction healing of the prior UNCONDITIONAL claim: the
FF-screening route for $\cW_N$ is obstructed by an explicit
cohomology class whose coefficient matches an independent universal
invariant. Any future closure of
Conjecture~\ref{conj:n4-mc4-zero-generic-parameters} at the $\cW_N$
level must reproduce the coefficient $(\Psi-1)/\Psi$ at the
appropriate sector, or explain why the obstruction is absorbed by
the chosen SDR ambient. This is the falsification test for the
conjecture.
\end{remark}

\subsection*{Non-principal hook-type extension (parabolic screenings)}

\begin{conjecture}[Non-principal hook-type, $r\le N-3$]
\label{conj:n4-non-principal-hook}
\ClaimStatusConjectured
For non-principal~$\cW$-algebras $\cW^k(\mathfrak{sl}_N,f)$ of
hook-type with partition height~$r\le N-3$, a parabolic-screening
presentation in the Kac--Roan--Wakimoto~2003 and Arakawa~2007
framework supplies the set-theoretic identification
\[
\cW^k(\mathfrak{sl}_N,f_{\mathrm{hook},r})
\;=\;
\bigcap_{\alpha\in\Delta_P^+}
\ker Q_\alpha
\quad\subset\quad
V_{k'}(\mathfrak{l}_P)\otimes\cH^{\otimes n_P},
\]
with $P$ the parabolic corresponding to the hook partition,
$\mathfrak{l}_P$ the Levi, and $n_P$ the Heisenberg rank. The
conjecture is that this presentation extends to a chain-level
Steenrod--Denis--Restivo data $(\iota,p,h)$ on the bar complex
compatible with the MC4${}^0$ stage-to-stage lift, at generic~$k$.
\end{conjecture}

\begin{remark}[Status of the hook-type conjecture]
\label{rem:n4-non-principal-hook-status}
KRW03 and Arakawa07 prove the vertex-algebra presentation
$\cW^k(\mathfrak{sl}_N,f_{\mathrm{hook},r})=\bigcap_\alpha\ker Q_\alpha$
(Kazhdan filtration, Drinfeld--Sokolov existence); the chiral
Steenrod--Denis--Restivo data for the MC4${}^0$ lift is a chain-level
statement beyond the cited literature. Consequently the conjecture
is conditional on (a) an explicit chain-level SDR construction for the
parabolic screening intersection, and (b) resolution of the
chiral-coproduct obstruction of
Proposition~\ref{prop:mc4-zero-wakimoto-sdr-obstruction} restricted to
the parabolic sub-system (the obstruction cocycle $R_\alpha$ at a
parabolic root $\alpha\in\Delta_P^+$ may or may not inherit the
principal $(\Psi-1)/\Psi$ coefficient; at the parabolic level the
coefficient structure is an open computation).
\end{remark}

\subsection*{Subregular and minimal: reduction to class~C SDR}

Subregular $\cW$-algebras (e.g.~Bershadsky--Polyakov $\mathrm{BP}_k$)
and minimal~$\cW$-algebras reduce to the class~C $\beta\gamma$
SDR via the principal~$\cW_{N-2}\times\mathfrak{sl}_2\times\beta\gamma$
decomposition (subregular) and the coset decomposition (minimal).
The Arakawa convention is used throughout:
$c(\mathrm{BP}_k)=2-24(k+1)^2/(k+3)$ and
$K_{\mathrm{BP}}(k):=c(k)+c(-k-6)\equiv 196$ in~$\mathbb{Q}(k)$
(inscribed in Vol~I standalone \texttt{bp\_self\_duality.tex}
as \verb|thm:bp-koszul-conductor-polynomial|). Fateev--Lukyanov
convention gives $K^{\mathrm{FL}}_{\mathrm{BP}}(k)=[(2k+9)(3k+17)-(2k+3)(3k+1)]/(k+3)
= 50(k+3)/(k+3)\equiv 50$ in $\mathbb{Q}(k)$; both conventions produce
a level-independent polynomial-constant Koszul conductor, differing
only in numerical value ($196$ vs.\ $50$) through the choice of
central-charge normalisation, and describe the same algebra via
level reparametrisation.

\subsection*{Summary table (honest)}

After the chiral-coproduct obstruction audit, the row for $\Vir_c$
and $\cW_N$ is CONJECTURAL, not UNCONDITIONAL:
\begin{center}
\begin{tabular}{lcccc}
\toprule
Algebra & Filtration & Strong? & Generic status & Regime \\
\midrule
$V_k(\fg)$, $k \ne -h^\vee$ & conformal & yes & unconditional & MC4${}^+$ \\
$V_\Lambda$ & conformal & yes & unconditional & MC4${}^+$ \\
$\beta\gamma$ (fermion number) & fermion & yes & unconditional & MC4${}^+$ \\
$\Vir_c$, $c$ generic & conformal & yes & CONJECTURAL & MC4${}^0$ (SDR frontier) \\
$\cW_N$, $\Psi$ generic & conformal & yes & CONJECTURAL & MC4${}^0$ (FF obstruction) \\
$\cW(\mathfrak{sl}_N,f_{\mathrm{hook},r\le N-3})$ & conformal & yes & CONJECTURAL & parabolic (open) \\
$\mathrm{BP}_k$, subregular & conformal & yes & CONJECTURAL & reduction-to-$\beta\gamma$ prose \\
$V_{-h^\vee}(\fg)$ & conformal & yes & excluded (Feigin--Frenkel center) & wild \\
\bottomrule
\end{tabular}
\end{center}

The residual conjectural content of MC4 is thus: the MC4${}^0$ regime
for class-$\mathsf{M}$ principal (Virasoro, principal~$\cW_N$) pending
explicit chain-level SDR inscription and resolution of the Feigin--Frenkel
chiral-coproduct obstruction of
Proposition~\ref{prop:mc4-zero-wakimoto-sdr-obstruction}; non-principal
hook-type pending a chain-level SDR for the parabolic presentation;
subregular / minimal~$\cW$ pending a theorem-level reduction to the
class-C $\beta\gamma$ SDR (the present text supplies only a prose
observation); and $V_{-h^\vee}(\fg)$ (critical level), where the
Feigin--Frenkel centre forces $\rho=\infty$. These are genuine
remaining mathematics at the bar-complex chain level, not
completion-machinery plumbing.

\end{document}
