% programme_summary_sections2_4.tex
% Sections 2--4 of the programme summary paper
% To be merged with programme_summary_section1.tex
%
% Convention: this file is self-contained but uses the same
% preamble and macros as Section 1. For compilation, splice
% into the main document before \end{document}.

% ====================================================================
\section{Curvature and the genus tower}
\label{sec:curvature}
% ====================================================================

At genus~$0$ the bar complex is flat: $d^2 = 0$ is an
algebraic identity, equivalent to the Borcherds axiom.
On a family of curves of genus $g \ge 1$, this nilpotence
fails. The failure is controlled by a single scalar.

% ====================================================================
\subsection{The prime form and the period defect}
\label{ssec:prime-form}
% ====================================================================

On a compact Riemann surface~$\Sigma_g$ of genus~$g \ge 1$,
the function $z_1 - z_2$ has no global meaning: a
meromorphic function with a single simple zero must have a
simple pole. The \emph{prime form} $E(z_1, z_2)$, a
section of $K^{-1/2} \boxtimes K^{-1/2}$ vanishing to
first order along the diagonal, replaces it. The
genus-$g$ propagator
\begin{equation}\label{eq:genus-g-propagator}
\eta^{(g)}_{12}
\;=\;
d\log E(z_1, z_2)
+ \pi \sum_{\alpha,\beta = 1}^{g}
(\operatorname{Im}\Omega)^{-1}_{\alpha\beta}
\,\omega_\alpha(z_1)\,\bar\omega_\beta(z_2)
\end{equation}
is single-valued; the period correction couples to the
Hodge bundle $\mathbb{E} = R^0\pi_*\omega_\pi$ through
the period matrix~$\Omega$.

Three properties of~\eqref{eq:genus-g-propagator} constrain
the genus tower. First, the logarithmic derivative
$d\log E$ has conformal weight~$1$ in both variables,
regardless of the conformal weight of the field being
sewed: every edge of every graph sum at every genus uses
the standard Hodge bundle~$\mathbb{E}_1$. Second, the
period correction is harmonic in each variable and involves
$(\operatorname{Im}\Omega)^{-1}$, the Arakelov Green
function on~$\Sigma_g$. Third, the Arnold relation acquires
a defect proportional to the Arakelov form, and this defect
propagates into the bar differential.

% ====================================================================
\subsection{Curvature}
\label{ssec:curvature}
% ====================================================================

Let $\pi \colon \mathcal{C}_g \to \overline{\cM}_g$ be the
universal curve. On each fibre~$\Sigma_g$, the propagator
$\eta^{(g)}$ is single-valued but no longer closed: the
period correction has a $\bar\partial$-component, and the
Arnold relation fails. The fibrewise bar differential
satisfies
\begin{equation}\label{eq:d-squared-curvature}
d_{\mathrm{fib}}^{\,2}
\;=\;
\kappa(\cA) \cdot \omega_g\,,
\end{equation}
where $\omega_g$ is the Arakelov $(1,1)$-form on the fibre
and $\kappa(\cA) \in \Bbbk$ is the \emph{modular
characteristic}. The modular characteristic is intrinsic to
the chiral algebra; it is determined by the leading OPE
singularity and is visible already at genus~$0$ as the
$\Sigma_2$-coinvariant of the collision residue:
$\kappa(\cA) = \mathrm{av}(r(z))$.

The failure of $d^2 = 0$ at genus~$g \ge 1$ is not a defect
of the construction; it is the construction detecting global
geometry. Period integrals restore nilpotence: the
Gauss--Manin connection absorbs the fibrewise curvature, and
the total differential satisfies $D_g^2 = 0$. The
curvature~\eqref{eq:d-squared-curvature} is the
infinitesimal avatar of this restoration.

% ====================================================================
\subsection{The genus expansion}
\label{ssec:genus-expansion}
% ====================================================================

For a modular Koszul chiral algebra~$\cA$ with a single
generator (or more generally with all generators of the
same conformal weight), the genus-$g$ obstruction class
$\mathrm{obs}_g(\cA)$ is proportional to the top Chern class
of the Hodge bundle:
\begin{equation}\label{eq:genus-universality}
\mathrm{obs}_g(\cA)
\;=\;
\kappa(\cA) \cdot \lambda_g\,,
\qquad g \ge 1\,.
\end{equation}
The free energy $F_g(\cA) = \kappa(\cA) \cdot
\lambda_g^{\mathrm{FP}}$, where
\begin{equation}\label{eq:faber-pandharipande}
\lambda_g^{\mathrm{FP}}
\;=\;
\frac{2^{2g-1} - 1}{2^{2g-1}}
\cdot
\frac{|B_{2g}|}{(2g)!}
\end{equation}
is the Faber--Pandharipande coefficient ($B_{2g}$ the
$2g$-th Bernoulli number), packages the entire genus tower
into the Hirzebruch $\hat{A}$-class:
\begin{equation}\label{eq:ahat-generating}
\sum_{g=1}^{\infty}
F_g(\cA)\,\hbar^{2g-2}
\;=\;
\frac{\kappa(\cA)}{\hbar^2}
\bigl[\hat{A}(i\hbar) - 1\bigr]\,,
\qquad
\hat{A}(x) = \frac{x/2}{\sinh(x/2)}\,.
\end{equation}
At genus~$1$: $\lambda_1^{\mathrm{FP}} = 1/24$. At
genus~$2$: $\lambda_2^{\mathrm{FP}} = 7/5760$. The
universal ratio $F_2/F_1 = 7/240$ is independent
of~$\cA$. The series converges for
$|\hbar| < 2\pi$, the first zero of $\sin(\hbar/2)$.

The genus-$1$ identity
$\mathrm{obs}_1 = \kappa \cdot \lambda_1$
is unconditional: it holds for all modular Koszul chiral
algebras, regardless of the number or weights of their
generators. At genus $g \ge 2$, the story is more
delicate.

\begin{remark}[Multi-weight correction]
\label{rem:multi-weight}
For a chiral algebra with generators of distinct conformal
weights $h_1, \ldots, h_r$, the genus-$g$ free energy
decomposes as
\begin{equation}\label{eq:multi-weight-decomposition}
F_g(\cA)
\;=\;
\kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}
\;+\;
\delta F_g^{\mathrm{cross}}(\cA)\,,
\end{equation}
where $\delta F_g^{\mathrm{cross}}$ is a graph sum over
mixed-channel boundary graphs of~$\overline{\cM}_{g,0}$.
At genus~$1$, $\delta F_1^{\mathrm{cross}} = 0$
unconditionally. For uniform-weight algebras
($h_1 = \cdots = h_r$),
$\delta F_g^{\mathrm{cross}} = 0$ at all genera. For
multi-weight algebras at $g \ge 2$, the correction is
generically nonzero: for $\mathcal{W}_3$ at genus~$2$,
$\delta F_2^{\mathrm{cross}}(\mathcal{W}_3)
= (c + 204)/(16c) > 0$ for all $c > 0$.
\end{remark}

% ====================================================================
\subsection{The modular characteristic}
\label{ssec:kappa}
% ====================================================================

The modular characteristic $\kappa(\cA)$ is the single
scalar controlling the genus tower. It is computed from
genus-$0$ data alone: the leading coefficient of the OPE,
extracted through the bar construction.

\begin{table}[ht]
\centering
\caption{Modular characteristic for the standard families}
\label{tab:kappa}
\renewcommand{\arraystretch}{1.6}
\begin{tabular}{lcc}
\toprule
\textbf{Algebra $\cA$}
 & $\boldsymbol{\kappa(\cA)}$
 & \textbf{Shadow depth class} \\
\midrule
Heisenberg $\cH_k$
 & $k$
 & $\mathbf{G}$ \\
Affine Kac--Moody $\widehat{\fg}_k$
 & $\dfrac{\dim(\fg) \cdot (k + h^\vee)}{2h^\vee}$
 & $\mathbf{L}$ \\[4pt]
$\beta\gamma$ system
 & $c/2$
 & $\mathbf{C}$ \\
Virasoro $\Vir_c$
 & $c/2$
 & $\mathbf{M}$ \\
$\mathcal{W}_3^k(\mathfrak{sl}_3)$
 & $5c/6$
 & $\mathbf{M}$ \\
$\mathcal{W}_N^k(\mathfrak{sl}_N)$
 & $\displaystyle c \cdot \sum_{j=2}^{N}\frac{1}{j}$
 & $\mathbf{M}$ \\[4pt]
\bottomrule
\end{tabular}
\end{table}

The modular characteristic is additive under independent
sums ($\kappa(\cA \oplus \cA') = \kappa(\cA) + \kappa(\cA')$
when the mixed OPE vanishes) and constrained by Koszul
duality: $\kappa(\cA) + \kappa(\cA^!) = 0$ for
Kac--Moody and free-field algebras;
$\kappa(\Vir_c) + \kappa(\Vir_{26-c}) = 13$ for Virasoro.
In general, $\kappa(\cA) + \kappa(\cA^!) = \rho \cdot K$
for $\mathcal{W}$-algebras, where $\rho$ is the
anomaly ratio and $K$ the complementarity constant.

At the self-dual point ($c = 13$ for Virasoro), the
complementarity sum is symmetric:
$\kappa(\Vir_{13}) = 13/2 = \kappa(\Vir_{13}^!)$.
At the critical level ($k = -h^\vee$ for Kac--Moody),
$\kappa = 0$ and the bar complex is flat at all genera:
the content migrates from curvature to bar cohomology,
where it appears as the Feigin--Frenkel centre.


% ====================================================================
\section{The five main theorems}
\label{sec:five-theorems}
% ====================================================================

The bar construction of a chiral algebra on a curve produces
a factorization coalgebra on the Ran space of the curve.
The five main theorems describe what this coalgebra
determines: the Koszul dual, the original algebra,
the complementarity decomposition, the genus tower, and
the chiral Hochschild cohomology. Each theorem is a
projection of the universal Maurer--Cartan element
$\Theta_\cA$ (Section~\ref{sec:mc}).

% ====================================================================
\subsection{Theorem A: Verdier intertwining}
\label{ssec:thm-a}
% ====================================================================

\begin{theorem}[A]\label{thm:A}
Let\/ $\cA$ be a chiral algebra on a smooth projective
curve~$X$. There is an adjunction
\[
B
\;\colon\;
\mathrm{Alg}_{\mathrm{aug}}(\mathrm{Fact}(X))
\;\rightleftarrows\;
\mathrm{CoAlg}_{\mathrm{conil}}(\mathrm{Fact}(X))
\;\colon\;
\Omega
\]
between augmented factorization algebras and conilpotent
factorization coalgebras, with unit and counit the
universal twisting morphisms. Verdier duality on\/
$\Ran(X)$ intertwines the bar of\/~$\cA$ with the bar
of its Koszul dual:
\begin{equation}\label{eq:verdier}
\mathbb{D}_{\Ran}\bigl(B(\cA)\bigr)
\;\simeq\;
B(\cA^!)\,,
\end{equation}
as factorization coalgebras, or equivalently
$\mathbb{D}_{\Ran}(B(\cA)) \simeq \cA^!_\infty$
as the homotopy Koszul dual algebra.
\end{theorem}

The adjunction is formal: it requires only the augmented
factorization-algebra structure and the duality on~$\Ran(X)$.
The intertwining~\eqref{eq:verdier} is a deeper statement:
it says that the Verdier dual of the bar \emph{coalgebra}
is the bar of the Koszul dual \emph{algebra}. The
identification of the homotopy Koszul dual $\cA^!_\infty$
(retaining full chain-level data) with the strict Koszul
dual $\cA^! = (H^*(B(\cA)))^\vee$ (retaining only
cohomology) is the content of Theorem~A on the Koszul
locus, not a tautology.

% ====================================================================
\subsection{Theorem B: bar-cobar inversion}
\label{ssec:thm-b}
% ====================================================================

\begin{theorem}[B]\label{thm:B}
On the Koszul locus, the cobar of the bar recovers the
original algebra:
\begin{equation}\label{eq:inversion}
\Omega\bigl(B(\cA)\bigr)
\;\xrightarrow{\;\sim\;}
\;\cA\,.
\end{equation}
The counit of the bar-cobar adjunction is a
quasi-isomorphism of augmented factorization algebras.
\end{theorem}

Bar-cobar inversion is a round-trip, not a duality.
It does not produce the Koszul dual (that is Verdier
duality, Theorem~A); it does not produce the bulk
algebra (that is the chiral derived centre, Theorem~H).
It recovers~$\cA$ itself.

The proof proceeds by constructing a contracting homotopy
for the counit, using the PBW filtration as a control
parameter: the associated graded of the cobar complex
coincides with a cofree resolution of the PBW-graded
algebra, and the filtration spectral sequence degenerates
at~$E_2$. Convergence of the spectral sequence requires
the Koszul hypothesis; for non-Koszul algebras, bar-cobar
inversion requires completion.

% ====================================================================
\subsection{Theorem C: complementarity}
\label{ssec:thm-c}
% ====================================================================

\begin{theorem}[C]\label{thm:C}
For a Koszul pair $(\cA, \cA^!)$ on~$X$ and $g \ge 2$, the
complementarity complex
\[
\mathbf{C}_g(\cA)
\;:=\;
R\Gamma\bigl(\overline{\cM}_g,\, \mathcal{Z}_\cA\bigr)
\]
decomposes into homotopy eigenspaces of the Verdier
involution~$\sigma$:
\begin{equation}\label{eq:complementarity}
\mathbf{C}_g
\;\simeq\;
\mathbf{Q}_g(\cA) \;\oplus\; \mathbf{Q}_g(\cA^!)\,.
\end{equation}
The summands $\mathbf{Q}_g(\cA) =
\operatorname{fib}(\sigma - \mathrm{id})$
and\/ $\mathbf{Q}_g(\cA^!) =
\operatorname{fib}(\sigma + \mathrm{id})$ are
Lagrangian for the $(-1)$-shifted symplectic pairing
on\/~$\mathbf{C}_g$.
\end{theorem}

The eigenspace decomposition (C1) is unconditional: it
holds for all modular Koszul algebras at all genera. The
scalar identity $F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$
on each summand (C2) requires the uniform-weight hypothesis
at $g \ge 2$. The Lagrangian property, a
$(-1)$-shifted symplectic statement in the sense of
Pantev--To\"en--Vaqui\'e--Vezzosi, is conditional on
perfectness and nondegeneracy of the cyclic pairing.

% ====================================================================
\subsection{Theorem D: the modular characteristic}
\label{ssec:thm-d}
% ====================================================================

\begin{theorem}[D]\label{thm:D}
For a uniform-weight modular Koszul chiral algebra\/~$\cA$,
the genus-$g$ obstruction class satisfies
$\mathrm{obs}_g(\cA) = \kappa(\cA) \cdot \lambda_g$
for all\/ $g \ge 1$, where $\kappa(\cA)$ is a universal,
additive, duality-constrained scalar determined by the
genus-$0$ data of\/~$\cA$. The generating function is
the Hirzebruch $\hat{A}$-class
\textup{(}\eqref{eq:ahat-generating}\textup{)}.
At genus\/~$1$, the identity is unconditional: it holds
for all modular Koszul algebras regardless of weight
structure.
\end{theorem}

The universality is the point: no matter how complicated
the OPE structure, the genus tower is controlled by a
single number. Theorem~D is the all-genera identity on the
uniform-weight lane; at genus~$1$ it is unconditional
(Remark~\ref{rem:multi-weight}).

% ====================================================================
\subsection{Theorem H: chiral Hochschild cohomology}
\label{ssec:thm-h}
% ====================================================================

\begin{theorem}[H]\label{thm:H}
For a chirally Koszul algebra~$\cA$, the chiral Hochschild
cohomology
$\mathrm{ChirHoch}^*(\cA)
= H^*(C^{\bullet}_{\mathrm{ch}}(\cA, \cA), \delta)$
is polynomial with generators concentrated in degrees
$\{0, 1, 2\}$:
\[
\dim_\Bbbk \mathrm{ChirHoch}^*(\cA)
\;\le\; 4\,.
\]
\end{theorem}

The chiral derived centre
$Z^{\mathrm{der}}_{\mathrm{ch}}(\cA) =
C^{\bullet}_{\mathrm{ch}}(\cA, \cA)$ is the universal
bulk algebra: the algebra of operators in the interior
that act on the boundary algebra~$\cA$. Theorem~H
constrains its cohomology. For the Virasoro algebra,
the total dimension of $\mathrm{ChirHoch}^*(\Vir_c)$ is
at most~$4$; this is a finite-dimensionality statement,
not a polynomial-ring statement.

% ====================================================================
\subsection{The Koszulness meta-theorem}
\label{ssec:meta-theorem}
% ====================================================================

The hypothesis shared by Theorems~A--H is chiral
Koszulness: bar cohomology $H^*(B(\cA))$ concentrated in
bar degree~$1$. The meta-theorem characterizes this
condition in twelve equivalent ways, ten of which are
unconditional, one conditional, one partial.

\begin{theorem}[Koszulness characterization]
\label{thm:koszul-meta}
For a chiral algebra~$\cA$ on~$X$ with PBW filtration,
conditions \textup{(i)--(x)} are equivalent. Under
additional perfectness hypotheses, \textup{(xi)} is
equivalent. Condition \textup{(xii)} implies
\textup{(x)}; the converse is open.
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\cA$ is chirally Koszul.
\item The PBW spectral sequence collapses at\/~$E_2$.
\item The minimal $A_\infty$-model of $B(\cA)$
 is formal: $m_n = 0$ for $n \ge 3$.
\item Ext diagonal vanishing:
 $\operatorname{Ext}^{p,q}_\cA(\omega_X, \omega_X) = 0$
 for $p \ne q$.
\item The bar-cobar counit
 $\Omega(B(\cA)) \to \cA$ is a quasi-isomorphism.
\item The Barr--Beck--Lurie comparison is an equivalence.
\item Factorization homology
 $\int_{\Sigma_g}\!\cA$ is concentrated in degree~$0$
 for all~$g$.
\item $\mathrm{ChirHoch}^*(\cA)$ is polynomial in
 degrees $\{0, 1, 2\}$.
\item The Kac--Shapovalov determinant is nonzero in the
 bar-relevant range.
\item Restriction to every FM boundary stratum is
 acyclic outside degree~$0$.
\item[{\upshape (xi)}] Lagrangian criterion \textup{(conditional)}.
\item[{\upshape (xii)}] $\cD$-module purity
 \textup{(one-directional: (x) $\Rightarrow$ (xii))}.
\end{enumerate}
\end{theorem}

The circuit of unconditional equivalences runs through five
independent mathematical domains: PBW degeneration
(commutative algebra), $A_\infty$-formality (homotopical
algebra), Barr--Beck--Lurie (higher categories),
Kac--Shapovalov (representation theory), and FM boundary
acyclicity (algebraic topology). That these five conditions
define the same class of algebras is the depth of the
meta-theorem.


% ====================================================================
\section{The universal Maurer--Cartan element
 and the shadow tower}
\label{sec:mc}
% ====================================================================

The five theorems of Section~\ref{sec:five-theorems} are
projections of a single algebraic object: the universal
Maurer--Cartan element $\Theta_\cA$ of the modular
convolution algebra.

% ====================================================================
\subsection{The bar-intrinsic construction}
\label{ssec:bar-intrinsic}
% ====================================================================

The genus-completed bar differential
$D_\cA = \sum_{g \ge 0} \hbar^g\,d^{(g)}_\cA$
satisfies $D_\cA^2 = 0$ by the codimension-$2$ face
cancellation on $\overline{\cM}_{g,n}$ (the same mechanism
as~\S\ref{ssec:d-squared}, extended to all genera by Mok's
log Fulton--MacPherson compactification). Write
$d_0 = d^{(0)}_\cA$ for the genus-$0$ bar differential.

\begin{construction}[Bar-intrinsic MC element]
\label{constr:bar-intrinsic}
Define the positive-genus correction
\begin{equation}\label{eq:theta-def}
\Theta_\cA
\;:=\;
D_\cA - d_0
\;=\;
\sum_{g \ge 1}
\hbar^g\,d^{(g)}_\cA
\;\in\;
\prod_{g \ge 1}
\mathrm{CoDer}^{\mathrm{cyc}}
\bigl(B^{(g)}_X(\cA)\bigr)[1]\,.
\end{equation}
\end{construction}

\begin{theorem}\label{thm:theta-mc}
$\Theta_\cA$ is a Maurer--Cartan element of the modular
cyclic deformation complex:
\begin{equation}\label{eq:mc-equation}
d_0(\Theta_\cA)
+ \tfrac{1}{2}[\Theta_\cA, \Theta_\cA]
\;=\; 0\,.
\end{equation}
\end{theorem}

\begin{proof}[Proof sketch]
Expand $D_\cA^2 = (d_0 + \Theta_\cA)^2 = 0$.
Since $d_0^2 = 0$ (genus-$0$ bar flatness), the
remaining terms give
$d_0(\Theta_\cA) + \frac{1}{2}[\Theta_\cA, \Theta_\cA]
= 0$, which is the MC equation. The bracket is the
convolution bracket on the modular cyclic deformation
complex, inherited from stable-curve gluing; its square-zero
property is a formal consequence of $d_0^2 = 0$.
\end{proof}

The construction requires no restriction to simple Lie
symmetry, no one-channel hypothesis, and no tautological-line
support condition. It works for all modular Koszul chiral
algebras. The modular characteristic~$\kappa$, the cubic
shadow~$\mathfrak{C}$, and the quartic resonance
class~$\mathfrak{Q}$ are arity projections of this single
element:
\begin{equation}\label{eq:shadow-projections}
\kappa(\cA) = \pi_2(\Theta_\cA)\,,
\qquad
\mathfrak{C}(\cA) = \pi_3(\Theta_\cA)\,,
\qquad
\mathfrak{Q}(\cA) = \pi_4(\Theta_\cA)\,.
\end{equation}
Each arity projection carries more information than the
last; the full $\Theta_\cA$ carries all of it.

% ====================================================================
\subsection{The shadow obstruction tower}
\label{ssec:shadow-tower}
% ====================================================================

The arity-$r$ projection
$\mathrm{Sh}_r(\cA) := \pi_r(\Theta_\cA)$ is the $r$-th
shadow coefficient. The sequence $S_2 = \kappa$,
$S_3 = \alpha$, $S_4$, $S_5, \ldots$ constitutes the
\emph{shadow obstruction tower}. On any one-dimensional
primary slice~$L$ of the cyclic deformation complex, the
MC equation~\eqref{eq:mc-equation} imposes a quadratic
constraint.

\begin{theorem}[Riccati algebraicity]
\label{thm:riccati}
The weighted shadow generating function
$H(t) := \sum_{r \ge 2} r\,S_r\,t^r$
satisfies
\begin{equation}\label{eq:algebraic-relation}
H(t)^2 \;=\; t^4\,Q_L(t)\,,
\end{equation}
where
\begin{equation}\label{eq:shadow-metric}
Q_L(t)
\;=\;
(2\kappa + 3\alpha t)^2
\;+\;
2\Delta\,t^2\,,
\qquad
\Delta := 8\kappa S_4\,,
\end{equation}
is the \emph{shadow metric}: a quadratic polynomial in~$t$
determined by three genus-$0$ invariants
$(\kappa, \alpha, S_4)$.
The entire shadow obstruction tower on~$L$ is determined
by~$Q_L$.
\end{theorem}

The generating function $H(t) = t^2\sqrt{Q_L(t)}$ is
algebraic of degree~$2$. The shadow obstruction tower
is neither a Taylor expansion that might diverge nor a
formal power series requiring analytic continuation: it is
the expansion of an explicit algebraic function. The
MC equation, which a priori is an infinite system of coupled
nonlinear equations, reduces on each primary slice to a
single quadratic identity.

% ====================================================================
\subsection{The G/L/C/M classification}
\label{ssec:glcm}
% ====================================================================

The discriminant $\Delta = 8\kappa S_4$ of the shadow
metric forces a universal dichotomy.

\begin{definition}[Shadow depth classification]
\label{def:shadow-depth}
The \emph{shadow depth} of~$\cA$ is
$r_{\max}(\cA) := \sup\{r \ge 2 : S_r \ne 0\}$.
The shadow depth class is:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{clcl}
\toprule
\textbf{Class} & \textbf{Name} &
 $\boldsymbol{r_{\max}}$ & \textbf{Mechanism} \\
\midrule
$\mathbf{G}$ & Gaussian &
 $2$ & $Q_L$ perfect square, $\alpha = 0$ \\
$\mathbf{L}$ & Lie &
 $3$ & $Q_L$ perfect square, $\alpha \ne 0$ \\
$\mathbf{C}$ & Contact &
 $4$ & stratum separation \\
$\mathbf{M}$ & Mixed &
 $\infty$ & $\Delta \ne 0$: $Q_L$ irreducible \\
\bottomrule
\end{tabular}
\end{center}
\end{definition}

The mechanism: when $\Delta = 0$, the shadow metric is a
perfect square $Q_L(t) = (2\kappa + 3\alpha t)^2$ and
$\sqrt{Q_L}$ is polynomial: the tower terminates.
If $\alpha = 0$ it terminates at arity~$2$ (class~$\mathbf{G}$:
Heisenberg); if $\alpha \ne 0$ at arity~$3$
(class~$\mathbf{L}$: affine Kac--Moody). When
$\Delta \ne 0$, $\sqrt{Q_L}$ is irrational: the tower
runs forever (class~$\mathbf{M}$: Virasoro,
$\mathcal{W}_N$). Class~$\mathbf{C}$ ($\beta\gamma$)
escapes the dichotomy by stratum separation: the quartic
contact invariant lives on a charged stratum whose
self-bracket exits the complex by rank-one rigidity.

The four classes are a homotopy-invariant classification:
they coincide with the $L_\infty$-formality depth of the
transferred minimal model. Class~$\mathbf{G}$ is
$L_\infty$-formal (all higher brackets vanish).
Class~$\mathbf{L}$ has exactly one nontrivial Massey
product. Class~$\mathbf{C}$ has formality obstructions
through arity~$4$. Class~$\mathbf{M}$ is intrinsically
non-formal: no finite truncation of the $L_\infty$
structure is quasi-isomorphic to a dg~Lie algebra.

Archetypes:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{clll}
\toprule
\textbf{Class} & \textbf{Archetype}
 & $\boldsymbol{\kappa}$ & $\boldsymbol{\Delta}$ \\
\midrule
$\mathbf{G}$ & Heisenberg $\cH_k$
 & $k$ & $0$ \\
$\mathbf{L}$ & $\widehat{\fg}_k$
 & $\dim(\fg)(k{+}h^\vee)/(2h^\vee)$ & $0$ \\
$\mathbf{C}$ & $\beta\gamma$
 & $c/2$ & $0$ (stratum separation) \\
$\mathbf{M}$ & $\Vir_c$
 & $c/2$ & $40/(5c{+}22)$ \\
\bottomrule
\end{tabular}
\end{center}

For the Virasoro algebra, the quartic contact invariant is
$Q^{\mathrm{contact}}_{\Vir} = 10/[c(5c+22)]$ and the
critical discriminant is $\Delta_{\Vir} = 8 \cdot (c/2)
\cdot 10/[c(5c+22)] = 40/(5c+22)$. Every shadow
coefficient $S_r$ for $r \ge 5$ is a rational function
of~$c$ with poles only at $c = 0$ and $c = -22/5$:
\begin{align}
S_5 &= -\frac{48}{c^2(5c{+}22)}\,,
 &
S_6 &= \frac{80(45c{+}193)}{3\,c^3(5c{+}22)^2}\,,
 &
S_7 &= -\frac{2880(15c{+}61)}{7\,c^4(5c{+}22)^2}\,.
\label{eq:shadow-coefficients}
\end{align}
These are the fingerprints of a class-$\mathbf{M}$ algebra:
the shadow tower is infinite, alternating in sign, and
controlled by an irrational algebraic function.

% ====================================================================
\subsection{The gauge-gravity dichotomy}
\label{ssec:gauge-gravity}
% ====================================================================

The classification has a physical interpretation. At
$\kappa = 0$ the bar complex is flat at all genera:
the genus tower carries no curvature, the free energy
vanishes, and the content lives in bar cohomology. This
is the regime of gauge theory: the Feigin--Frenkel centre
(the Langlands dual of the affine algebra at critical level)
is the genus-$0$ bar cohomology $H^0(B(\widehat{\fg}_{-h^\vee}))$.

At $\kappa \ne 0$ the bar complex is curved: every genus
contributes a nonzero obstruction class, the genus tower
is nontrivial, and the free energy is the $\hat{A}$-genus.
This is the regime of gravity: the bar curvature is the
perturbative genus expansion.

The Koszul duality $\cA \leftrightarrow \cA^!$ exchanges
gauge and gravity sectors. For affine Kac--Moody at
generic level, $\kappa(\widehat{\fg}_k) \ne 0$ and the
algebra is curved; at the Koszul-dual critical level
$k' = -k - 2h^\vee$, $\kappa(\widehat{\fg}_{k'}) \ne 0$
as well, and both sides are gravitational. The gauge regime
(critical level, $\kappa = 0$) is the fixed locus of a
one-parameter family.

For the Virasoro algebra, the Koszul dual is
$\Vir_c^! = \Vir_{26-c}$. The gauge locus is $c = 0$
(topological: $\kappa = 0$); the gravitational locus is
$c \ne 0$. The self-dual point $c = 13$
($\kappa = 13/2 = \kappa^!$) is the critical string.
The Clifford algebra of the complementarity pairing
degenerates at $c = 26$ ($\kappa(\Vir_0^!) = 0$):
the $26$-dimensional bosonic string is the critical point
where the Koszul dual becomes flat.

The dichotomy gauge/$\kappa{=}0$ vs
gravity/$\kappa{\ne}0$ is not a physical input: it is a
theorem about the bar complex. The physical interpretation
follows from the identification of bar curvature with
perturbative genus expansions in quantum field theory.

\end{document}
