\documentclass[11pt,reqno]{amsart}

% ================================================================
% Packages
% ================================================================
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathrsfs}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{booktabs}
\usepackage{array}
\usepackage{microtype}
\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks=true,linkcolor=blue!60!black,citecolor=green!40!black,urlcolor=blue!60!black]{hyperref}
\usepackage[all]{xy}

% ================================================================
% Theorem environments
% ================================================================
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{construction}[theorem]{Construction}
\newtheorem{example}[theorem]{Example}
\newtheorem{principle}[theorem]{Principle}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% ================================================================
% Macros (providecommand: safe against collision with any input)
% ================================================================
\providecommand{\cA}{\mathcal{A}}
\providecommand{\cB}{\mathcal{B}}
\providecommand{\cC}{\mathcal{C}}
\providecommand{\cD}{\mathcal{D}}
\providecommand{\cE}{\mathcal{E}}
\providecommand{\cF}{\mathcal{F}}
\providecommand{\cG}{\mathcal{G}}
\providecommand{\cH}{\mathcal{H}}
\providecommand{\cI}{\mathcal{I}}
\providecommand{\cJ}{\mathcal{J}}
\providecommand{\cK}{\mathcal{K}}
\providecommand{\cL}{\mathcal{L}}
\providecommand{\cM}{\mathcal{M}}
\providecommand{\cN}{\mathcal{N}}
\providecommand{\cO}{\mathcal{O}}
\providecommand{\cP}{\mathcal{P}}
\providecommand{\cQ}{\mathcal{Q}}
\providecommand{\cR}{\mathcal{R}}
\providecommand{\cS}{\mathcal{S}}
\providecommand{\cT}{\mathcal{T}}
\providecommand{\cU}{\mathcal{U}}
\providecommand{\cV}{\mathcal{V}}
\providecommand{\cW}{\mathcal{W}}
\providecommand{\cX}{\mathcal{X}}
\providecommand{\cY}{\mathcal{Y}}
\providecommand{\cZ}{\mathcal{Z}}
\providecommand{\barB}{\bar{B}}
\providecommand{\barC}{\overline{C}}
\providecommand{\Defcyc}{\mathrm{Def}_{\mathrm{cyc}}}
\providecommand{\Ran}{\mathrm{Ran}}
\providecommand{\MC}{\mathrm{MC}}
\providecommand{\Sym}{\mathrm{Sym}}
\providecommand{\Hom}{\mathrm{Hom}}
\providecommand{\Ext}{\mathrm{Ext}}
\providecommand{\Res}{\mathrm{Res}}
\providecommand{\Aut}{\mathrm{Aut}}
\providecommand{\FM}{\overline{C}}
\providecommand{\fg}{\mathfrak{g}}
\providecommand{\fh}{\mathfrak{h}}
\providecommand{\gmod}{\mathfrak{g}^{\mathrm{mod}}_\cA}
\providecommand{\gAmod}{\mathfrak{g}^{\mathrm{mod}}_\cA}
\providecommand{\Sh}{\mathrm{Sh}}
\providecommand{\OPE}{\mathrm{OPE}}
\providecommand{\Vir}{\mathrm{Vir}}
\providecommand{\Ahat}{\widehat{A}}
\providecommand{\hol}{\mathrm{hol}}
\providecommand{\bC}{\mathbb{C}}
\providecommand{\bP}{\mathbb{P}}
\providecommand{\bA}{\mathbb{A}}
\providecommand{\bZ}{\mathbb{Z}}
\providecommand{\bR}{\mathbb{R}}
\providecommand{\bQ}{\mathbb{Q}}
\providecommand{\Bbbk}{\mathbb{k}}
\providecommand{\coll}{\mathrm{coll}}
\providecommand{\FP}{\mathrm{FP}}
\providecommand{\cross}{\mathrm{cross}}
% Operad/algebra macros
\providecommand{\Ass}{\mathrm{Ass}}
\providecommand{\Com}{\mathrm{Com}}
\providecommand{\SCchtop}{\mathrm{SC}^{\mathrm{ch,top}}}
\providecommand{\Convinf}{\mathrm{Conv}_\infty}
\providecommand{\Convstr}{\mathrm{Conv}_{\mathrm{str}}}
\providecommand{\Ainf}{A_\infty}
\providecommand{\ChirHoch}{\mathrm{ChirHoch}}
\providecommand{\Defcyc}{\mathrm{Def}_{\mathrm{cyc}}}
\providecommand{\orline}[1]{\mathfrak{o}_{#1}}
\providecommand{\fsl}{\mathfrak{sl}}
\providecommand{\HH}{\mathrm{HH}}
\providecommand{\Fun}{\mathrm{Fun}}
\providecommand{\Op}{\mathrm{Op}}
\providecommand{\Rep}{\mathrm{Rep}}
\providecommand{\End}{\mathrm{End}}
\providecommand{\Conf}{\mathrm{Conf}}
% Subscript/superscript decorators
\providecommand{\coll}{\mathrm{coll}}
\providecommand{\dg}{\mathrm{dg}}
\providecommand{\FP}{\mathrm{FP}}
\providecommand{\KZ}{\mathrm{KZ}}
\providecommand{\conn}{\mathrm{conn}}
\providecommand{\bF}{\mathbb{F}}
\providecommand{\der}{\mathrm{der}}
\providecommand{\ch}{\mathrm{ch}}
\providecommand{\op}{\mathrm{op}}
\providecommand{\oc}{\mathrm{oc}}
\providecommand{\SC}{\mathrm{SC}}
\providecommand{\Id}{\mathrm{Id}}
\providecommand{\id}{\mathrm{id}}
\providecommand{\Reg}{\mathrm{Reg}}
\providecommand{\GM}{\mathrm{GM}}
\providecommand{\co}{\mathrm{co}}
\providecommand{\contact}{\mathrm{contact}}
\providecommand{\cross}{\mathrm{cross}}
\providecommand{\grav}{\mathrm{grav}}
\providecommand{\sep}{\mathrm{sep}}
\providecommand{\nsep}{\mathrm{nsep}}
\providecommand{\DS}{\mathrm{DS}}
\providecommand{\BV}{\mathrm{BV}}
\providecommand{\cyc}{\mathrm{cyc}}
\renewcommand{\mod}{\mathrm{mod}}
\providecommand{\ann}{\mathrm{ann}}
\providecommand{\fib}{\mathrm{fib}}
\providecommand{\Fl}{\mathrm{Fl}}
\providecommand{\sgn}{\mathrm{sgn}}
\providecommand{\Coder}{\mathrm{Coder}}
\providecommand{\Ob}{\mathrm{Ob}}
\providecommand{\Obs}{\mathrm{Obs}}
\providecommand{\clutch}{\mathrm{clutch}}
\providecommand{\Ch}{\mathrm{Ch}}
\providecommand{\red}{\mathrm{red}}
\providecommand{\gh}{\mathrm{gh}}
\providecommand{\fo}{\mathfrak{o}}
\providecommand{\CompCl}{\mathrm{CompCl}}
\providecommand{\Tr}{\mathrm{Tr}}
\providecommand{\Conv}{\mathrm{Conv}}

\DeclareMathOperator{\gr}{gr}
\DeclareMathOperator{\rk}{rk}
\DeclareMathOperator{\depth}{depth}
\DeclareMathOperator{\Spec}{Spec}

\numberwithin{equation}{section}

% ================================================================
% Graceful fallback for cross-references to theorems/propositions
% that live in the full monograph but are cited in this standalone
% survey. Undefined labels resolve to "full monograph" rather than
% the default LaTeX "??" placeholder.
% ================================================================
\makeatletter
\let\svy@oldref\ref
\renewcommand{\ref}[1]{%
 \@ifundefined{r@#1}{\textit{full monograph}}{\svy@oldref{#1}}%
}
\makeatother

% ================================================================
\begin{document}

\title[Modular Koszul Duality: A Survey]
{Modular Koszul Duality and the Shadow Obstruction Tower:\\
A Survey}

\author{Raeez Lorgat}
\address{Perimeter Institute for Theoretical Physics,
 Waterloo, ON N2L 2Y5, Canada}
\email{rlorgat@perimeterinstitute.ca}

\date{\today}

\begin{abstract}
We study holomorphic chiral factorisation (co)homology via bar and
cobar chain constructions at various geometric locations on algebraic
curves. $E_n$-chiral algebras at all operadic levels ($n=1,2,3,\infty$)
are factorisation algebras on configuration spaces, inherently
geometric; the ordered bar complex
$\barB^{\mathrm{ord}}(\cA)=T^c(s^{-1}\bar\cA)$ with deconcatenation
coproduct, $R$-matrix, and Yangian structure is the categorical
logarithm. The bar differential squares to zero by Arnold plus
Borcherds at genus zero and acquires curvature
$\kappa(\cA)\cdot\omega_g$ from the Hodge bundle at higher genus.
A single universal Maurer--Cartan element $\Theta_{\cA}$ controls the
genus tower. Five theorems (A--D, H) organise the invariants:
bar--cobar adjunction with Verdier intertwining, inversion on the
Koszul locus, complementary Lagrangian decomposition, the modular
characteristic, and polynomial chiral Hochschild cohomology
concentrated in degrees $\{0,1,2\}$. The shadow obstruction tower
partitions the standard landscape into four depth classes
(Gaussian/Lie/contact/mixed). The derived chiral centre
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ carries $E_2$/$E_3$
structure; its physical realisation as the bulk algebra of a 3d
holomorphic--topological gauge theory gives rise to line operators,
spectral braiding, and the bulk-boundary-line triangle, with 3d
quantum gravity as the climax. Calabi--Yau quantum groups (CoHA,
quantum toroidal algebras) are the concrete $E_1$-chiral quantum
groups constructed from CY geometry via 6d holomorphic Chern--Simons
and related theories. We survey the $E_n$ hierarchy and operadic
circle, the seven faces of the collision residue, the arithmetic of
the shadow $L$-function, the open/closed bridge to 3d HT-QFT, modular
PVA quantization, holographic reconstruction, and the outstanding
frontier conjectures across three volumes totalling ${\sim}4{,}800$
pages.
\end{abstract}

\subjclass[2020]{17B69, 14H10, 18M70, 81T40}

\keywords{Chiral algebras, bar construction, Koszul duality,
moduli of curves, vertex algebras, Maurer--Cartan,
W-algebras, factorization algebras, Yangian, shadow tower}

\maketitle

\tableofcontents

\bigskip

% ====================================================================
% TRACK A: sections 1--6 (bar construction, curvature, modular homotopy,
% universal Maurer--Cartan, tangent complex, shadow obstruction tower)
% ====================================================================

\section*{1.\quad The ordered bar complex}
% ====================================================================

\medskip

\noindent
The primitive object of this programme is the \emph{ordered bar
complex} $\barB^{\mathrm{ord}}(\cA)=T^c(s^{-1}\bar\cA)$, an
$E_1$-coalgebra with deconcatenation coproduct, built on ordered
configurations of points on an algebraic curve. The symmetric bar
$\barB^{\Sigma}(\cA)$, and with it every statement about the modular
characteristic~$\kappa$ and the shadow obstruction tower, is the
$\Sigma_n$-coinvariant shadow obtained by averaging. The ordered bar
carries the full $R$-matrix, the Yangian, the braiding; averaging
collapses this profile to a scalar. What survives averaging is the
subject of the five theorems; what is lost is the subject of the
$E_1$ frontier.

The exposition constructs the ordered bar first, computes its
chain-level structure on explicit examples, extracts the
$R$-matrix as the degree-$2$ collision residue, and only then
derives the symmetric bar by projection. No symmetric-bar result
is stated without first exhibiting the $E_1$ object it descends from.

\subsection*{1.1.\enspace The $1$-form}

Let $X$ be a smooth algebraic curve over~$\mathbf C$. On the
configuration space $C_2(X)=X\times X\setminus\Delta$, define the
logarithmic $1$-form
\begin{equation}\label{eq:preface-eta}
\eta_{12}\;=\;d\log(z_1-z_2)\;=\;\frac{dz_1-dz_2}{z_1-z_2}.
\end{equation}
This form has a simple pole along~$\Delta$ with residue~$1$. The
residue depends on no coordinate, no metric, no level. A double
pole~$dz/(z-w)^2$ transforms under coordinate change and has no
coordinate-independent residue; a regular $1$-form extracts nothing
from the collision. The logarithmic derivative is the unique $1$-form
on $C_2(X)$ with a first-order pole along~$\Delta$ and conformally
invariant residue.

On $C_3(X)$, the three pullbacks $\eta_{12}, \eta_{23}, \eta_{31}$
satisfy the \emph{Arnold relation}
\begin{equation}\label{eq:preface-arnold}
\eta_{12}\wedge\eta_{23}+\eta_{23}\wedge\eta_{31}+\eta_{31}\wedge\eta_{12}\;=\;0,
\end{equation}
the differential-form image of the partial-fractions identity
$\tfrac{1}{(z_1-z_2)(z_2-z_3)}+\tfrac{1}{(z_2-z_3)(z_3-z_1)}+\tfrac{1}{(z_3-z_1)(z_1-z_2)}=0$.
Arnold proved that~\eqref{eq:preface-arnold}, replicated across all
triples $\{i,j,k\}\subset\{1,\ldots,n\}$, generates the complete ideal
of relations in $H^*(\mathrm{Conf}_n(\mathbf C),\mathbf C)$.

Under $z\mapsto w(z)$ the propagator transforms as
$\eta_{ij}\mapsto\eta_{ij}+d\log\frac{w(z_i)-w(z_j)}{z_i-z_j}$;
near the diagonal this reduces to $d\log w'(z_i)$, the standard
$\mathrm{Diff}(X)$ cocycle. The propagator is a BRST ghost for
diffeomorphisms.

\subsection*{1.2.\enspace The ordered bar complex on~$X$}

A \emph{chiral algebra}~$\cA$ on a smooth algebraic curve~$X$ is a
$\mathcal D_X$-module equipped with a chiral bracket
$\mu^{\mathrm{ch}}\colon j_*j^*(\cA\boxtimes\cA)\to\Delta_!(\cA)$
extracting the singular part of sections with poles along the diagonal.
In local coordinates this encodes the operator product expansion
$a(z)\,b(w)\sim\sum_{n\ge 0}a_{(n)}b(w)/(z-w)^{n+1}$,
governed by the Borcherds identity coupling all pole orders.

Place sections $a_1,\dots,a_n\in\cA$ at distinct ordered points
$z_1<\cdots<z_n$ on~$X$ and assign to each consecutive pair
the form $\eta_{i,i+1}=d\log(z_i-z_{i+1})$. The
Fulton--MacPherson compactification
$\overline{\mathrm{FM}}_n(X)$ resolves $\mathrm{Conf}_n(X)$ by
iterated real oriented blowup along all diagonal strata (a blowup,
not a complement); boundary codimension-one faces are indexed by
subsets $S\subseteq\{1,\ldots,n\}$ with $|S|\ge 2$.

The \emph{ordered chiral bar complex}:
\begin{equation}\label{eq:ordered-bar}
\barB^{\mathrm{ord}}_X(\cA)
\;=\;
\bigoplus_{n\ge 1}(s^{-1}\bar\cA)^{\otimes n}\otimes
\Gamma\bigl(\overline{\mathrm{FM}}_n(X),\Omega^{n-1}_{\log}\bigr).
\end{equation}
Here $\bar\cA=\ker(\varepsilon\colon\cA\to\omega_X)$ is the
augmentation ideal, $T^c(V)=\bigoplus_{n\ge 0}V^{\otimes n}$ is the
cofree tensor coalgebra, and $s^{-1}$ is desuspension with
$|s^{-1}a|=|a|-1$ in cohomological convention ($|d|=+1$).

This is the primitive object. It carries the \emph{deconcatenation
coproduct}
\[
\Delta[s^{-1}a_1|\cdots|s^{-1}a_n]
=\sum_{i=0}^n[s^{-1}a_1|\cdots|s^{-1}a_i]\otimes[s^{-1}a_{i+1}|\cdots|s^{-1}a_n],
\]
splitting an ordered sequence at every position: $n+1$ terms for an
ordered $n$-tuple. This makes $\barB^{\mathrm{ord}}(\cA)$ an
$E_1$-coalgebra: coassociative, not cocommutative. The linear
ordering of the points is retained; there is no $\Sigma_n$-quotient.
Its $E_1$-Koszul dual $\cA^!_{\mathrm{line}}$ governs the category
of line operators: for affine Kac--Moody,
$\cA^!_{\mathrm{line}}$ is the Yangian $Y(\fg)$.

The differential decomposes as
$d_{\barB}=d_{\mathrm{int}}+d_{\mathrm{res}}+d_{\mathrm{dR}}$:
the internal differential of~$\cA$, the OPE residue extraction
along codimension-one boundary strata of $\overline{\mathrm{FM}}_n(X)$,
and the de Rham differential on logarithmic forms.

\subsection*{1.3.\enspace $d^2=0$: Arnold kills the form, Borcherds kills the algebra}

Expand $(d_{\mathrm{int}}+d_{\mathrm{res}}+d_{\mathrm{dR}})^2$. The
diagonal terms: $d_{\mathrm{int}}^2=0$, $d_{\mathrm{dR}}^2=0$; the
cross-terms $[d_{\mathrm{int}},d_{\mathrm{dR}}]=0$ by Leibniz. The
remaining terms pair into three cancellation mechanisms:

\emph{Disjoint supports}: when $\{i,j\}\cap\{k,l\}=\emptyset$ the
boundary faces are transverse, and the residue operators commute.

\emph{Shared index}: when $\{i,j\}\cap\{k,l\}=\{j=k\}$ the triple
collision $z_i=z_j=z_l$ lies in a codimension-two stratum. The
form contribution $\eta_{ij}\wedge\eta_{jl}$ paired with its cyclic
partners vanishes by the Arnold relation~\eqref{eq:preface-arnold};
the corresponding algebraic contractions vanish by Borcherds.
Arnold kills the form; Borcherds kills the algebra; both are consumed.

\emph{Same pair}: $d_{\mathrm{res}}^{(ij)}\,d_{\mathrm{res}}^{(ij)}=0$
by the desuspension sign rule.

Result: $d_{\barB}^2=0$ iff the $n$-th products satisfy the Borcherds
identity. The ordered bar construction accepts exactly chiral algebras.

All of this is genus~$0$. At genus $g\ge 1$ the propagator acquires
quasi-periodicity from the prime form, and $d_{\mathrm{fib}}^2\neq 0$:
the curvature $d_{\mathrm{fib}}^2=\kappa(\cA)\cdot\omega_g$ is a
single scalar times the Hodge class, governing the entire genus
expansion.

\subsection*{1.4.\enspace The collision residue and the $R$-matrix}

The ordered bar differential extracts OPE data at each collision
stratum. At tensor degree~$2$ the extraction is the \emph{collision
residue}: the residue of the OPE integrated against the propagator
$\eta_{12}=d\log(z_1-z_2)$. Since $d\log$ has a simple pole, it
absorbs one pole order from the OPE:
\begin{equation}\label{eq:pole-absorption}
\text{pole order of }r(z) \;=\; \text{pole order of OPE} - 1.
\end{equation}
The result is the \emph{classical $r$-matrix}
\[
r(z)\;=\;\operatorname{Res}^{\mathrm{coll}}_{0,2}
\bigl(\Theta^{E_1}_{\cA}\bigr),
\]
a matrix-valued rational function encoding the full binary OPE data
of the ordered bar. The Yang--Baxter equation
$[r_{12},r_{13}]+[r_{12},r_{23}]+[r_{13},r_{23}]=0$ is the
Arnold relation~\eqref{eq:preface-arnold} evaluated on the
Casimir: three boundary divisors of $\overline{\mathrm{FM}}_3(\bC)$,
three terms.

The $r$-matrix is an $E_1$ invariant. The symmetric bar sees only
its $\Sigma_2$-coinvariant scalar shadow:
$\kappa(\cA)=\mathrm{av}(r(z))$ for abelian and Virasoro-type
families, while non-abelian affine Kac--Moody adds the Sugawara
shift $\dim(\fg)/2$. This lossy projection is the subject
of~\S1.7.

\subsection*{1.5.\enspace Chain-level: the Heisenberg ordered bar}

The Heisenberg algebra $\cH_k$: one field~$\alpha$ of conformal
weight~$1$, $\alpha(z)\alpha(w)\sim k/(z-w)^2$. Only
$\alpha_{(1)}\alpha=k\cdot\mathbf 1$ is nonzero.

\medskip
\noindent\textbf{Degree~$2$.}\enspace
The ordered bar at tensor degree~$2$ is
$\barB^{\mathrm{ord}}_2=\bC\cdot[s^{-1}\alpha|s^{-1}\alpha]
\otimes\Gamma(\overline{\mathrm{FM}}_2,\Omega^1_{\log})$.
The residue differential acts by
\[
d_{\mathrm{res}}
\bigl(s^{-1}\alpha\otimes s^{-1}\alpha\otimes\eta_{12}\bigr)
\;=\;k\cdot\mathbf{1}.
\]
The OPE has pole order~$2$; the $d\log$ kernel absorbs one order,
producing a simple-pole residue. This is the complete degree-$2$
ordered bar data.

\medskip
\noindent\textbf{Degree~$3$.}\enspace
At tensor degree~$3$,
$\barB^{\mathrm{ord}}_3=(s^{-1}\alpha)^{\otimes 3}
\otimes\Omega^2(\overline{\mathrm{FM}}_3)$.
Every collision stratum extracts
$\alpha_{(1)}\alpha=k\cdot\mathbf{1}$, leaving $n-2$ copies
of~$\alpha$. Since $\mathbf{1}_{(p)}\alpha=0$ for all $p\ge 0$,
no further contraction occurs: the degree-$3$ differential
vanishes identically. The Arnold relation kills the form-level
contribution independently. All higher degrees vanish by the same
mechanism.

\medskip
\noindent\textbf{Bar cohomology.}\enspace
The bar complex is quadratic: all structure is captured at tensor
degree~$2$. Bar cohomology concentrates in degree~$1$:
$H^1(\barB(\cH_k))=\bC\cdot\alpha^*$, $H^n=0$ for $n\ge 2$.
The conformal-weight-graded bar Hilbert series is rational.
The partition-graded generating function is transcendental:
$\prod_{m\ge 1}(1-x^m)^{-1}$, reflecting the Fock-space grading
of the single generator. $\cH_k$ is chirally Koszul.

\medskip
\noindent\textbf{$R$-matrix and averaging.}\enspace
The ordered $r$-matrix: $r^{\cH}(z)=k/z$, a scalar (the OPE double
pole $k/(z-w)^2$ drops to a simple pole under $d\log$ absorption).
The spectral $R$-matrix $R(z)=\exp(k/z)$ is already
$\Sigma_2$-invariant: averaging loses nothing.
\begin{equation}\label{eq:av-heisenberg}
\mathrm{av}\bigl(r^{\cH}(z)\bigr)=k=\kappa(\cH_k).
\end{equation}
Koszul dual:
$\cH_k^!=(\operatorname{Sym}^{\mathrm{ch}}(V^*),m_0=-k\,\omega)$,
a curved symmetric chiral algebra with $m_1^2(a)=[m_0,a]$.
Complementarity (free-field branch, sum $=0$; contrast Virasoro where sum $=13$): $\kappa(\cH_k)+\kappa(\cH_k^!)=k+(-k)=0$.

\subsection*{1.6.\enspace Chain-level: the Kac--Moody ordered bar}

The affine Kac--Moody algebra $\widehat\fg_k$ for simple~$\fg$
of rank~$\ell$ and dual Coxeter number~$h^\vee$:
\[
J^a(z)J^b(w)\sim\frac{f^{ab}{}_{c}J^c(w)}{z-w}
+\frac{k\kappa^{ab}}{(z-w)^2}.
\]
Two pole orders. The first carries the Lie bracket
$J^a_{(0)}J^b=f^{ab}{}_cJ^c$; the second carries the invariant
form $J^a_{(1)}J^b=k\kappa^{ab}\cdot\mathbf 1$.

\medskip
\noindent\textbf{Degree~$2$: two components.}\enspace
The ordered bar differential at tensor degree~$2$ decomposes as
\[
d_{\barB}\bigl([s^{-1}J^a|s^{-1}J^b]\otimes\eta_{12}\bigr)
\;=\;
\underbrace{f^{ab}{}_{c}\,[s^{-1}J^c]}_{\text{Lie bracket (simple pole)}}
\;+\;
\underbrace{k\kappa^{ab}\cdot\mathbf{1}}_{\text{curvature (double pole)}}.
\]
The Lie bracket contributes a Chevalley--Eilenberg-type
differential; the inner product contributes the curvature.
The coexistence of both poles, absent in the pure double-pole
Heisenberg, makes $\widehat\fg_k$ the first nontrivial example.

\medskip
\noindent\textbf{Degree~$3$: Serre relations.}\enspace
For $\fg=\mathfrak{sl}_3$ with simple roots $\alpha_1,\alpha_2$ and
generators $E_1,E_2$, the degree-$3$ ordered bar complex
$\barB^{\mathrm{ord}}_3=\fg^{\otimes 3}\otimes\Omega^2(\overline{\mathrm{FM}}_3)$
has dimension $8^3\times 2=1024$.
The Serre element
\[
S=[E_1|E_1|E_2]-2[E_1|E_2|E_1]+[E_2|E_1|E_1]
\]
is a bar cycle: $d_{\barB}(S\otimes\eta_{12}\wedge\eta_{13})=0$.
This is the Serre relation $(\mathrm{ad}\,E_1)^2(E_2)=0$ manifesting
as a degree-$3$ bar cocycle. The two independent Serre relations
(for $\{i,j\}=\{1,2\}$) generate
$H^3(\barB(\widehat{\mathfrak{sl}}_{3,k}))$ at generic level.

\medskip
\noindent\textbf{Bar cohomology across Kac--Moody.}\enspace
The bar cohomology of affine Kac--Moody algebras exhibits the full
range of algebraic complexity:
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{llll}
\textbf{Algebra} & $\dim H^n(\barB)$ & \textbf{Growth}
 & \textbf{Generating function}\\ \hline
$\widehat{\mathfrak{sl}}_2$ & $2n+1$ & linear
 & rational: $x(3-x)/(1-x)^{2}$\\
$\widehat{\mathfrak{sl}}_3$ & $\{8,36,204,\ldots\}$ & exponential
 & rational: $4x(2{-}13x{-}2x^2)/((1{-}8x)(1{-}3x{-}x^2))$\\
$\widehat\fg_k$ (general) & Garland--Lepowsky & polynomial ($\fg$ simple)
 & D-finite
\end{tabular}
\end{center}
For $\widehat{\mathfrak{sl}}_2$, the linear growth
$\dim H^n=2n+1$ is the Garland--Lepowsky concentration: bar
cohomology is generated in degree~$1$ by the $3$-dimensional
adjoint representation. For $\widehat{\mathfrak{sl}}_3$, the
rational generating function with denominator $(1-8x)(1-3x-x^2)$
reflects the Serre relations at degree~$3$; the PBW spectral sequence
collapses at~$E_2$.

\medskip
\noindent\textbf{$R$-matrix and averaging.}\enspace
The ordered $r$-matrix is the level-prefixed Casimir:
\[
r^{\mathrm{KM}}(z)\;=\;k\,\Omega/z,
\qquad\Omega=\sum_a J^a\otimes J_a
\]
(at $k=0$ the $r$-matrix vanishes; at $k=-h^\vee$ it is critical).
Averaging collapses the Casimir tensor to its trace, with a Sugawara
shift from simple-pole self-contraction:
\begin{equation}\label{eq:av-km}
\mathrm{av}(k\,\Omega/z)
\;=\;\frac{k\dim\fg}{2h^\vee}
\;=\;\kappa_{\mathrm{dp}},
\qquad
\kappa(\widehat\fg_k)
\;=\;\kappa_{\mathrm{dp}}+\frac{\dim\fg}{2}
\;=\;\frac{(k+h^\vee)\dim\fg}{2h^\vee}.
\end{equation}
The $\dim(\fg)/2$ term is the Sugawara shift: the
simple-pole self-contraction through the adjoint Casimir eigenvalue
$2h^\vee$. For $\widehat{\mathfrak{sl}}_2$:
$\kappa=3(k+2)/4$; for $\widehat{\mathfrak{sl}}_3$:
$\kappa=4(k+3)/3$.

The Casimir tensor structure $\Omega=\sum_a J^a\otimes J_a$, invisible
to~$\kappa$, is the data that builds the Yangian $Y(\fg)$.
Koszul dual: $\widehat\fg_k^!=\widehat\fg_{-k-2h^\vee}$
(Feigin--Frenkel duality). Complementarity:
$\kappa(\widehat\fg_k)+\kappa(\widehat\fg_k^!)=0$
(KM branch: sum $=0$; Virasoro branch: sum $=13$).

\subsection*{1.7.\enspace The averaging map: from ordered to symmetric}

The symmetric bar
$\barB^{\Sigma}(\cA)=\operatorname{Sym}^c(s^{-1}\bar\cA)$
is the $\Sigma_n$-coinvariant quotient of the ordered bar, with the
coshuffle coproduct: $2^n$ bipartitions of an unordered set rather
than $n+1$ consecutive splittings. This is an $E_\infty$-coalgebra,
the Beilinson--Drinfeld factorization coalgebra on $\mathrm{Ran}(X)$.
Its Koszul dual $\cA^!_{\mathrm{ch}}$ is the Francis--Gaitsgory
chiral Koszul dual via Verdier duality on $\operatorname{Ran}(X)$.

The averaging map
\[
\mathrm{av}\colon\barB^{\mathrm{ord}}(\cA)\longrightarrow\barB^{\Sigma}(\cA)
\]
takes $\Sigma_n$-coinvariants. For a chiral algebra with OPE poles,
this descent uses the spectral $R$-matrix as twisting datum.
Applying $\mathrm{av}$ at each degree:
\begin{equation}\label{eq:av-organizing}
\begin{aligned}
\text{degree }2\colon&\quad\mathrm{av}(r(z))+\kappa_{\mathrm{sp}}=\kappa(\cA)
 &&\text{(Theorem D; $\kappa_{\mathrm{sp}}=0$ for abelian, $\dim\fg/2$ for KM)},\\
\text{degree }3\colon&\quad\mathrm{av}(\text{KZ associator})
 =\mathfrak{C}
 &&\text{(cubic shadow)},\\
\text{degree }4\colon&\quad\mathrm{av}(\text{Yangian coproduct})
 =\mathfrak{Q}
 &&\text{(quartic resonance class)}.
\end{aligned}
\end{equation}
Each degree-$n$ component of the ordered Maurer--Cartan element
$\Theta^{E_1}_\cA$ projects under $\mathrm{av}$ to the degree-$n$
shadow. The full obstruction tower is the coinvariant image of
the ordered tower.

\medskip
\noindent\textbf{What averaging loses.}\enspace
For Heisenberg, $r(z)=k/z$ is already symmetric: averaging loses
nothing. For Kac--Moody, $r(z)=k\,\Omega/z$ carries the Casimir
tensor $\Omega=\sum_a J^a\otimes J_a$; averaging collapses
$\Omega$ to $\dim(\fg)/(2h^\vee)$ and discards the tensor structure
that generates the Yangian $Y(\fg)$, the braided monoidal structure
on line operators, and the RTT relations. For Virasoro,
$r(z)=(c/2)/z^3+2T/z$ carries the stress-tensor coupling at
degree~$2$; averaging collapses it to $\kappa=c/2$ and discards the
higher-spin data.

In each case: the ordered bar carries the $R$-matrix, the Yangian
lineage, the braiding. The symmetric bar carries~$\kappa$, the
shadow tower, the genus expansion. The first is the full algebra;
the second is its scalar fingerprint.

\subsection*{1.8.\enspace The five theorems as averaged invariants}

The main theorems are the invariants of
$\Theta^{E_1}_{\cA}$ that survive $\Sigma_n$-coinvariant projection.

\medskip
\noindent\textbf{Theorem A} (bar-cobar adjunction and Verdier
intertwining). The cobar functor $\Omega(\barB(\cA))$ inverts
the bar construction on the Koszul locus:
$\Omega(\barB(\cA))\xrightarrow{\sim}\cA$. Verdier duality on
$\mathrm{Ran}(X)$ sends the factorization coalgebra
$\barB_X^\Sigma(\cA)$ to the homotopy Koszul
dual~$\cA^!_\infty$, a factorization algebra whose cohomology
recovers $\cA^!$. This identification intertwines bar-cobar
inversion with Verdier duality.

\medskip
\noindent\textbf{Theorem B} (bar-cobar inversion). On the Koszul
locus, the counit $\varepsilon\colon\Omega(\barB(\cA))\to\cA$ is a
quasi-isomorphism at every genus. Koszulness is characterised by
twelve equivalent conditions (\S9).

\medskip
\noindent\textbf{Theorem C} (complementarity). The ordered
partition functions $Q^{E_1}_{g,n}(\cA)$ and $Q^{E_1}_{g,n}(\cA^!)$
sum to a topological invariant. The coinvariant projection
yields the scalar complementarity $\kappa(\cA)+\kappa(\cA^!)=K(\cA)$,
where $K=0$ for Kac--Moody and free fields, $K=13$ for Virasoro.

\medskip
\noindent\textbf{Theorem D} (modular characteristic). The
genus-$1$ formula
$\mathrm{obs}_1(\cA)=\kappa(\cA)\cdot\lambda_1$ is
unconditional for every family.
On the proved uniform-weight lane, the all-genera extension
$\mathrm{obs}_g(\cA)=\kappa(\cA)\cdot\lambda_g$ holds via
clutching morphisms on $\partial\overline{\cM}_g$
(the clutching-uniqueness step is the principal conditional
element; an independent GRR derivation provides an
alternative path).
Multi-weight $g\ge 2$ requires the cross-channel correction
$\delta F_g^{\mathrm{cross}}$.

\medskip
\noindent\textbf{Theorem H} (chiral Hochschild).
$\mathrm{ChirHoch}^*(\cA)$ has polynomial Hilbert series,
concentrated in cohomological degrees $\{0,1,2\}$.

\subsection*{1.9.\enspace Bar chain models on curve geometries}

To understand a chiral algebra is to construct its bar complex on
every relevant curve geometry. Each geometry reveals a different
algebraic structure.

\medskip
\noindent\textbf{The formal disk $D$.}\enspace
The local model. The chiral endomorphism operad
$\End^{\mathrm{ch}}_\cA$ is
$\Aut(\cO)$-equivariant, and the bar differential encodes the
OPE via mode products $a_{(n)}b$. For Heisenberg:
$B_D(\cH_k) = T^c(s^{-1}\Bbbk[J])$ with
$d[s^{-1}J|s^{-1}J] = k$.

\medskip
\noindent\textbf{The punctured disk $D^*$.}\enspace
At homology level, $H^{\mathrm{ch}}_*(D^*, \cA) \cong
\mathrm{HH}_*(\cA)$ (state-field correspondence). At
\emph{chain level}, $C^{\mathrm{ch}}_*(D^*, \cA)$ carries the
full holomorphic structure (OPE poles, spectral parameters,
$E_2$ data), while $C^{\mathrm{top}}_*(S^1, \cA)$ carries only
topological $E_1$ data. The chain-level comparison $D^*$ versus
$S^1$ is the $E_2 - E_1$ gap.

\medskip
\noindent\textbf{The annulus $A_{r_1, r_2}$.}\enspace
Two boundary circles: bimodule structure. The annular bar
$B^{\ann}(\cA)$ computes sewing and the topological Hochschild bimodule.
Pinching the waist gives the pair-of-pants degeneration. For
Heisenberg: $B^{\ann}(\cH_k)$ gives the partition function
$\mathrm{tr}(q^{L_0 - c/24}) = 1/\eta(\tau)$.

\medskip
\noindent\textbf{Nodal curves.}\enspace
On boundary strata of $\overline\cM_{g,n}$: each stable graph
vertex contributes a component bar complex, each edge contributes
the sewing kernel (thin-annulus limit of $B^{\ann}$). Curvature
$d_{\mathrm{fib}}^2 = \kappa \cdot \omega_g$ arises from failure
to extend across nodes.

\medskip
\noindent\textbf{The pair of pants.}\enspace
The multiplication cobordism $\bP^1 \setminus \{0,1,\infty\}$.
Its bar chain model encodes fusion: three collision channels, the
Arnold relation forcing consistency. For Kac--Moody, the
pair-of-pants bar encodes the fusion tensor product via the KZ
equation on three-point conformal blocks.

\subsection*{1.10.\enspace The $E_n$-chiral hierarchy
and derived centres}

$E_n$-chiral algebras are factorisation algebras and are inherently
geometric. $E_\infty$-chiral algebras (all standard vertex algebras)
live on $\Ran(X)$; the symmetric bar $\barB^\Sigma$ is their bar
complex. $E_1$-chiral algebras live on $\Ran^{\ord}(X)$; the ordered
bar $\barB^{\ord}$ carries the $R$-matrix. The formality bridge
(Theorem~\ref{thm:e1-formality-bridge}): for $E_\infty$-input,
ordered and symmetric bars are quasi-isomorphic. The formality
failure (Theorem~\ref{thm:e1-formality-failure}): for genuinely
$E_1$-input (Yangians, Etingof--Kazhdan quantum vertex algebras),
ordered chiral homology has dimension $n!$ at degree~$n$, while the
symmetric quotient collapses to dimension~$1$.

The chiral quantum group equivalence
(Theorem~\ref{thm:chiral-qg-equiv}): on the Koszul locus, three
structures determine each other---the spectral $R$-matrix, the
chiral $A_\infty$ structure, and the chiral coproduct. Concrete
verifications through $\mathfrak{gl}_N$ for all $N \ge 1$
(Theorem~\ref{thm:glN-chiral-qg}).

The derived chiral centre
$\cZ^{\der}_{\ch}(\cA) = C^\bullet_{\ch}(\cA, \cA)$ carries $E_2$
structure from $E_1$ input (Deligne conjecture) and $E_3$ from
$E_2$ input (higher Deligne). Theorem~H: concentration in
degrees $\{0,1,2\}$ with polynomial Hilbert series. The
$\SCchtop$ structure lives on the pair
$(\cZ^{\der}_{\ch}(\cA),\, \cA)$: bulk acting on boundary. The bar
complex $\barB(\cA)$ is a single-coloured $E_1$ coalgebra, NOT an
$\SCchtop$-coalgebra.

The $E_3$ identification (Theorem~\ref{thm:e3-identification}): for
simple $\fg$, $\cZ^{\der}_{\ch}(V_k(\fg)) \cong A^\lambda$ as
$E_3$-families over $\lambda \cdot H^3(\fg)[[\lambda]]$. The
topologisation theorem
(Theorem~\ref{thm:topologization}): $\SCchtop + \text{conformal
vector} \simeq E_3^{\mathrm{top}}$.

All of this is algebraic-geometric: configuration spaces,
FM compactifications, Mok's logarithmic spaces. Volume~II
interprets these constructions physically: the derived centre IS
the bulk of a 3d gauge theory.

\subsection*{1.11.\enspace The $E_n$ operadic circle}

The $E_n$ circle $E_3^{\mathrm{top}} \to E_2 \to E_1 \to E_2
\to E_3^{\mathrm{top}}$ is an algebraic-geometric structure:
five functorial operations between categories of factorisation
algebras on configuration spaces.

Arrow~1 ($E_3 \to E_2$): restriction from the bulk to a
codimension-$2$ defect. Arrow~2 ($E_2 \to E_1$): passage to the
ordered bar. Arrow~3 ($E_1 \to E_2$): the Drinfeld centre
$\cZ\colon E_1\text{-}\mathsf{Cat} \to
E_2\text{-}\mathsf{Cat}$, the sole source of non-trivial
braiding ($\pi_1(\mathrm{Conf}_2(\bR^3)) = 0$ makes direct
$E_3 \to E_2$ restriction always symmetric). Arrow~4
($E_2 \to E_3$): derived centre via higher Deligne. Arrow~5
($E_3 = E_3$): the closing, conjectural
(Conjecture~\ref{conj:v1-drinfeld-center-equals-bulk}). The
circle partly closes: the $E_3$ identification
(Theorem~\ref{thm:e3-identification}) proves
$\cZ^{\der}_{\ch}(V_k(\fg)) \cong A^\lambda$ for simple~$\fg$.

Volume~II interprets the circle physically: the derived centre
IS the bulk of a 3d gauge theory. Volume~III constructs concrete
$E_1$-chiral quantum groups from CY geometry (CoHA, quantum
toroidal algebras) that feed the circle at Arrow~2.

\begin{remark}[The zero-dimensional shadow]\label{rem:preface-zero-dim}
When $X=\operatorname{Spec}\Bbbk$ is a point, configuration spaces
collapse, logarithmic forms vanish, and the chiral bar complex reduces
to the classical bar construction of an associative algebra.
Classical Koszul duality (Priddy, Beilinson--Ginzburg--Soergel,
Loday--Vallette) embeds on $X=\bA^1$: the affine line
deformation-retracts to a point (but the retraction is additional
data, not a canonical identification; on~$\bP^1$ the global topology
has no counterpart over a bare point).
\end{remark}

Everything above takes place at genus~$0$: the propagator is globally
defined on $\bP^1$, and the Arnold relation holds without correction.
On a curve of genus $g\ge 1$, $z_1-z_2$ has no global meaning; the
Arnold relation acquires a defect, the bar differential no longer
squares to zero, and the defect is controlled by a single scalar.


% ====================================================================
\section*{2.\quad Curvature and the genus tower}
% ====================================================================

The genus-zero bar complex is exact: $d_{\mathrm{fib}}^2=0$ by Arnold
and Borcherds. At genus $g\ge 1$ the bar differential acquires
curvature from the Hodge bundle, and the resulting genus tower carries
the scalar modular characteristic $\kappa(\cA)$, the $\hat A$-genus
generating function, complementarity, and the Feigin--Frenkel
involution. Every formula in this section begins with the Heisenberg
computation ($\kappa=k$, the level) and deforms through Kac--Moody
($\kappa=(k+h^\vee)\dim\fg/(2h^\vee)$) to Virasoro ($\kappa=c/2$).

\subsection*{2.1.\enspace The genus-$g$ propagator}

The genus-$0$ propagator $\eta_{12}=d\log(z_1-z_2)$ relied on
$z_1-z_2$ being a globally defined function on $\bP^1$. On a compact
curve of genus $g\ge 1$, any meromorphic function with a simple zero
must also have a pole: $z_1-z_2$ has no global meaning. The
replacement is the \emph{prime form}
$E(z_1,z_2)$: a section of $K^{-1/2}\boxtimes K^{-1/2}$
vanishing to first order along the diagonal with no other zeros. The
bundle is $K^{-1/2}\boxtimes K^{-1/2}$; the prime form is a
$(-\tfrac12,-\tfrac12)$-differential. In a local coordinate with
diagonal $z_1=z_2$,
\[
E(z_1,z_2)=(z_1-z_2)\bigl(1+O(z_1-z_2)\bigr)\cdot(dz_1)^{-1/2}(dz_2)^{-1/2}.
\]
Analytic continuation around the $B$-cycle $B_j$ in~$z_1$ gives
\[
E(z_1+B_j,z_2)=-\exp\bigl(-\pi i\Omega_{jj}-2\pi i\textstyle\int_{z_2}^{z_1}\omega_j\bigr)\cdot E(z_1,z_2),
\]
where $\Omega=(\Omega_{jk})$ is the period matrix and
$\omega_1,\ldots,\omega_g$ the holomorphic differentials normalised by
$\oint_{A_j}\omega_k=\delta_{jk}$. The $A$-cycle monodromy is trivial.

The logarithmic derivative
$\omega(z_1,z_2):=d_{z_1}\log E(z_1,z_2)$ is the fundamental
meromorphic differential of the second kind. The \emph{genus-$g$
propagator}:
\[
\eta^{(g)}_{12}=d\log E(z_1,z_2)+\pi\sum_{j,k=1}^g(\operatorname{Im}\Omega)^{-1}_{jk}\operatorname{Im}\!\Bigl(\int_{z_2}^{z_1}\omega_j\Bigr)\omega_k(z_1).
\]
The period correction $(\operatorname{Im}\Omega)^{-1}_{jk}$ compensates
$B$-cycle monodromy, rendering $\eta^{(g)}_{12}$ single-valued; this
is a full $g\times g$ matrix at genus $g\ge 2$, never collapsed to a
scalar. The price:
$\eta^{(g)}_{12}$ is no longer holomorphic. The propagator couples to
the Hodge bundle $\mathbb E\to\overline{\mathcal M}_g$ through
$\Omega$.

\medskip
\noindent\textbf{The prime form at genus~$1$.}\enspace
At genus~$1$, the curve is the elliptic curve $\bC/(\bZ+\bZ\tau)$
with $\operatorname{Im}\tau>0$, and the prime form reduces to the
Jacobi theta function:
\[
E(z_1,z_2)=\frac{\theta_1(z_1-z_2\,|\,\tau)}{\theta_1'(0\,|\,\tau)}\cdot(dz_1)^{-1/2}(dz_2)^{-1/2}.
\]
The period matrix is the scalar $\Omega=\tau$; the genus-$1$ propagator
\[
\eta^{(1)}_{12}=d_{z_1}\log\theta_1(z_1-z_2\,|\,\tau)+\frac{\pi}{\operatorname{Im}\tau}\operatorname{Im}(z_1-z_2)\,dz_1
\]
has a single simple pole along the diagonal $z_1=z_2$ (from the
zero of $\theta_1$) and is single-valued under both $A$- and $B$-cycle
translation. The logarithmic derivative
$\partial_{z_1}\log\theta_1(z\,|\,\tau)=\wp_1(z\,|\,\tau)$ is the
Weierstrass zeta variant (the ratio $\theta_1'/\theta_1$, periodic
under $z\mapsto z+1$, quasi-periodic under $z\mapsto z+\tau$ with
increment $-2\pi i$). The period correction renders the propagator
single-valued at the cost of holomorphicity.

\medskip
\noindent\textbf{The prime form at genus~$2$.}\enspace
At genus~$2$, the period matrix $\Omega=\bigl(\begin{smallmatrix}\tau_1&\tau_3\\\tau_3&\tau_2\end{smallmatrix}\bigr)$
is a $2\times 2$ symmetric matrix in the Siegel upper half-space
$\mathfrak{H}_2$. The prime form is constructed from the genus-$2$
theta function with an odd half-characteristic. The period correction
matrix $(\operatorname{Im}\Omega)^{-1}$ is now a genuine $2\times 2$
inverse:
\[
(\operatorname{Im}\Omega)^{-1}=\frac{1}{\operatorname{Im}\tau_1\operatorname{Im}\tau_2-(\operatorname{Im}\tau_3)^2}\begin{pmatrix}\operatorname{Im}\tau_2&-\operatorname{Im}\tau_3\\-\operatorname{Im}\tau_3&\operatorname{Im}\tau_1\end{pmatrix}.
\]
This matrix never degenerates to a scalar; formulas written at genus~$1$
by replacing $1/\operatorname{Im}\tau$ with $(\operatorname{Im}\Omega)^{-1}_{jk}$
must be verified at $g=2$ in full matrix form.

\medskip
\noindent\textbf{The propagator has weight~$1$.}\enspace
The bar propagator $\eta^{(g)}_{12}=d\log E(z_1,z_2)+\text{(period correction)}$
is a $(1,0)$-form in $z_1$ for every genus. It has weight~$1$, never
weight~$h$ (the conformal weight of a field). The $d\log$ absorbs one
power of the local coordinate from the prime form, producing a
meromorphic differential with a simple pole along the diagonal. This
weight-$1$ property is genus-independent: the period correction is
smooth and does not change the pole structure. Any formula with a bar
propagator of weight $\neq 1$ is wrong.

\subsection*{2.2.\enspace Curvature}

The Arnold relation at genus~$g$ acquires a defect. The period
corrections produce a residual $(1,1)$-form, and the fibrewise bar
differential satisfies
\begin{equation}\label{eq:pref-curvature}
d_{\mathrm{fib}}^{2}\;=\;\kappa(\cA)\cdot\omega_g,
\end{equation}
where $\omega_g$ is the Arakelov $(1,1)$-form on the fibre of the
universal curve $\pi\colon\mathcal C_g\to\overline{\mathcal M}_g$, and
$\kappa(\cA)\in\Bbbk$ is the \emph{modular characteristic}, determined
entirely by the leading OPE singularity. The class $\omega_g$ lives on
the fibre $\Sigma_g$, not on the moduli space $\overline{\cM}_g$; its
pushforward $\pi_*\omega_g=c_1(\mathbb E)=\lambda_1$ lands in
$H^2(\overline{\cM}_g)$.

Two conventions coexist. The bar differential $d_{\mathrm{bar}}^2=0$
\emph{always}, at every genus: the bar construction is a dg coalgebra
by definition. The fiberwise differential $d_{\mathrm{fib}}^2=\kappa\cdot\omega_g$
is a statement about the fibrewise restriction of the bar complex
to a single curve $\Sigma_g$: on that fibre, the Arnold relations
fail by a $(1,1)$-correction from the period matrix. The total
differential $D_\cA$ incorporates the Gauss--Manin connection and
squares to zero globally. This three-level structure
(bar = exact; fibrewise = curved; total = exact) controls every
formula in the genus tower.

\medskip
\noindent\textbf{Curvature computation: Heisenberg.}\enspace
The Heisenberg OPE $J(z)J(w)\sim k/(z-w)^2$ has $r$-matrix
$r^{\mathrm{Heis}}(z)=k/z$ (trace-form convention; at $k=0$, $r=0$).
The curvature arises from the failure of $\eta^{(g)}\wedge\eta^{(g)}$
to vanish: at genus~$0$, Arnold gives
$\eta_{12}\wedge\eta_{23}+\eta_{23}\wedge\eta_{31}+\eta_{31}\wedge\eta_{12}=0$;
at genus~$g\ge 1$, the period correction in $\eta^{(g)}$ contributes
a $(1,1)$-residual proportional to $\omega_g$.

Every residue extraction from the double-pole OPE gives
$\alpha_{(1)}\alpha=k$, with no structure-constant contributions (the
algebra is abelian). The curvature is the trace of this operation over
the one-dimensional bar cohomology:
\[
\kappa(\cH_k)=\mathrm{tr}\!\left(\frac{r^{\mathrm{Heis}}(z)}{z}\bigg|_{z=0}\right)=k.
\]
Sanity checks: $k=0$ gives $\kappa=0$ (uncurved, the free boson with
no kinetic term). $k=1$ gives $\kappa=1$, matching the central
charge $c_{\mathrm{Heis}}(k{=}1)=1$. The formula $\kappa(\cH_k)=k$
is the simplest instance of the modular characteristic: the level
\emph{is} the curvature.

\medskip
\noindent\textbf{Curvature computation: Kac--Moody.}\enspace
For $\widehat{\fg}_k$, the curvature receives the
trace over the adjoint representation:
\[
\kappa(\widehat{\mathfrak g}_k)=\frac{(k+h^\vee)\dim\mathfrak g}{2h^\vee}.
\]
The derivation proceeds by the averaging map identity. In the
trace-form convention, the $r$-matrix is $r^{\mathrm{KM}}(z)=k\Omega/z$,
where $\Omega=\sum_a t^a\otimes t^a$ is the Casimir of the Killing
form (at $k=0$, $r=0$; correct). The double-pole channel
gives $\mathrm{av}(r(z))=k\dim\fg/(2h^\vee)$. The simple-pole
self-contraction through the adjoint Casimir eigenvalue $2h^\vee$
contributes an additional $\dim\fg/2$. Together:
\[
\kappa(\widehat\fg_k)=\underbrace{\frac{k\dim\fg}{2h^\vee}}_{\text{double-pole}}+\underbrace{\frac{\dim\fg}{2}}_{\text{simple-pole Sugawara shift}}=\frac{(k+h^\vee)\dim\fg}{2h^\vee}.
\]
Sanity checks: $k=0$ gives $\kappa=\dim\fg/2$ (not zero; the
Lie bracket persists and the simple-pole channel contributes).
$k=-h^\vee$ gives $\kappa=0$ (critical level: Sugawara undefined,
curvature vanishes, bar complex uncurved).

For $\fsl_2$: $\dim\fg=3$, $h^\vee=2$, so
$\kappa(\widehat{\fsl}_{2,k})=3(k+2)/4$. At $k=1$:
$\kappa=9/4$. At $k=-2$ (critical): $\kappa=0$.

At the critical level $k=-h^\vee$ the shifted level vanishes and the
bar complex is uncurved. The Sugawara construction is undefined (the
central charge $c=k\dim\mathfrak g/(k+h^\vee)$ has a pole) but the
curvature parameter vanishes.

\medskip
\noindent\textbf{Curvature computation: Virasoro.}\enspace
For Virasoro at central charge~$c$, the OPE is
$T(z)T(w)\sim\tfrac{c/2}{(z-w)^4}+\tfrac{2T(w)}{(z-w)^2}+\tfrac{\partial T(w)}{z-w}$.
The bar propagator absorbs one pole order (the $d\log$ shifts pole
order by one: $\mathrm{pole}_r=\mathrm{pole}_{\mathrm{OPE}}-1$), so
the collision residue is $r^{\mathrm{Vir}}(z)=(c/2)/z^3+2T/z$
(cubic plus simple, not quartic). The averaging map extracts the
scalar from the simple-pole channel and the cubic-pole channel:
\[
\kappa(\mathrm{Vir}_c)=\mathrm{av}(r^{\mathrm{Vir}}(z))=c/2.
\]
Sanity checks: $c=0$ gives $\kappa=0$ (uncurved). $c=1$
gives $\kappa=1/2$. $c=13$ gives $\kappa=13/2$ (the self-dual
point under Koszul duality).

The Koszul dual is $\mathrm{Vir}_{26-c}$, with
$\kappa(\mathrm{Vir}_{26-c})=(26-c)/2$; the two sum to~$13$, not zero.
At $c=13$, Virasoro is self-dual under Koszul duality.

\medskip
\noindent\textbf{Curvature computation: $\cW_N$.}\enspace
The principal $\cW_N$-algebra has generators at conformal weights
$\{2,3,\ldots,N\}$ (that is, $N-1$ generators; the highest weight
is $N$, not $N+1$). The modular characteristic is
\[
\kappa(\cW_{N,c})=c\cdot(H_N-1),\qquad H_N=\sum_{j=1}^N\frac{1}{j},
\]
where $H_N$ is the harmonic number (with upper limit $N$, not $N-1$).
Sanity check: at $N=2$, $H_2-1=1/2$, so $\kappa(\cW_2)=c/2$,
matching the Virasoro formula ($\cW_2=\mathrm{Vir}$). At $N=3$,
$H_3-1=5/6$, so $\kappa(\cW_3)=5c/6$.

\subsection*{2.3.\enspace Period integrals restore nilpotence}

The curvature~\eqref{eq:pref-curvature} obstructs $d_{\mathrm{fib}}^2=0$
but not the total $D_g^2=0$. Integration against $A$-cycle periods
defines a connection on the family of bar complexes parametrised by
$\overline{\mathcal M}_g$. The corrected total differential
\[
D_g=d_{\mathrm{fib}}+\nabla^{\mathrm{GM}}
\]
incorporates the Gauss--Manin connection on the Hodge bundle, and
$D_g^2=0$: the $(1,1)$-curvature of the fibrewise differential is
absorbed by the $(0,1)$-part of the base connection. The fibrewise
class $\kappa\cdot\omega_g\in H^{1,1}(\mathcal C_g)$ is identified
under the period map $\overline{\mathcal M}_g\to\mathcal A_g$ with
the $(0,1)$-curvature of $\nabla^{\mathrm{GM}}$ on $R^1\pi_*\mathbb C$,
and the two curvatures cancel.

\medskip
\noindent\textbf{The cancellation mechanism.}\enspace
Write the total differential as $D_g=d_{\mathrm{fib}}+\nabla^{\GM}$.
Then
\begin{align*}
D_g^2&=d_{\mathrm{fib}}^2+\{d_{\mathrm{fib}},\nabla^{\GM}\}+(\nabla^{\GM})^2\\
&=\kappa\cdot\omega_g+0+(-\kappa\cdot\omega_g)=0.
\end{align*}
The cross-term $\{d_{\mathrm{fib}},\nabla^{\GM}\}=0$ holds because
$d_{\mathrm{fib}}$ acts on the fibre and $\nabla^{\GM}$ acts on the
base; the two commute by the product structure of the universal curve
(locally). The Gauss--Manin curvature $(\nabla^{\GM})^2=-\kappa\cdot\omega_g$
follows from the Kodaira--Spencer identification: the obstruction
to extending a flat section of $\mathbb E$ across moduli is precisely
the Hodge class $c_1(\mathbb E)$, with coefficient $\kappa$.

\medskip
\noindent\textbf{Heisenberg: period integrals as Eisenstein
series.}\enspace
For $\cH_k$ at genus~$1$, the propagator is
$\eta^{(1)}_{12}=d_{z_1}\log\theta_1(z_1-z_2|\tau)+(\pi/\operatorname{Im}\tau)\operatorname{Im}(z_1-z_2)dz_1$.
The period integral $\oint_{A}(\eta^{(1)})^{2n}$ produces the
Eisenstein series $G_{2n}(\tau)=(2n{-}1)!!\cdot E_{2n}(\tau)$ as
Taylor coefficients of the Green's function expansion near the
diagonal: the bar complex at genus~$1$ knows the ring of
quasi-modular forms $\bC[E_2^*,E_4,E_6]$. The quasi-modular
$E_2^*(\tau)=E_2(\tau)-3/(\pi\operatorname{Im}\tau)$ is the
genus-$1$ propagator itself; the almost-holomorphic correction is
the period term.

\medskip
\noindent\textbf{Kac--Moody: the KZB connection.}\enspace
For $\widehat\fg_k$, the Gauss--Manin connection on the bar complex
over $\overline{\cM}_{1,n}$ is the Knizhnik--Zamolodchikov--Bernard
(KZB) connection. The heat equation
\[
\frac{\partial}{\partial\tau}\Phi=\frac{1}{4\pi i(k+h^\vee)}\sum_{a}\frac{\partial^2}{\partial z_a^2}\Phi+\text{(interaction terms)}
\]
expresses the flatness $D_g^2=0$ as the joint system of KZ (in $z$)
and heat (in $\tau$) equations. The Sugawara denominator
$k+h^\vee$ in the prefactor is the same factor that appears in
$\kappa=(k+h^\vee)\dim\fg/(2h^\vee)$: the curvature and the
connection are controlled by a single parameter.

\subsection*{2.4.\enspace The genus tower (uniform weight)}

The bar complex traces a family of curved cochain complexes over
$\overline{\mathcal M}_g$. For \emph{uniform-weight} algebras
(single-generator, or multi-generator with all generators of the same
conformal weight), the obstruction to flatness is the characteristic
class
\begin{equation}\label{eq:obs-uniform}
\operatorname{obs}_g(\cA)=\kappa(\cA)\cdot\lambda_g\in H^*(\overline{\mathcal M}_g),\qquad\lambda_g=c_g(\mathbb E),
\qquad \end{equation}
where $\mathbb E=\pi_*\omega_\pi$ is the Hodge bundle: the vector
bundle on $\overline{\mathcal M}_g$ whose fibre over $[C]$ is the
$g$-dimensional space $H^0(C,\omega_C)$. At genus~$1$ the
factorization holds unconditionally for all families. For
\emph{multi-weight} families at genus~$g\ge 2$ the scalar formula
\emph{fails}: a cross-channel correction from mixed-propagator
boundary graphs appears,
\begin{equation}\label{eq:obs-multiweight}
\operatorname{obs}_g(\cA)=\kappa(\cA)\cdot\lambda_g+\delta F_g^{\mathrm{cross}},\qquad\text{(all-weight)}
\end{equation}
(multi-weight genus expansion theorem, full monograph). Every
appearance of $\operatorname{obs}_g$, $F_g$, or $\lambda_g$ in this
monograph carries explicit tagging: \textsc{(uniform-weight)} or
\textsc{(all-weight, with cross-channel correction)}.

Grothendieck--Riemann--Roch applied to the universal curve
$\pi\colon\mathcal C_g\to\overline{\mathcal M}_g$ computes the total
obstruction: the Chern character of $R\pi_*\omega_\pi$ involves the
Todd class of the relative tangent, the $\hat A$-genus. The
generating function in the uniform-weight lane:
\[
\sum_{g\ge 1}\operatorname{obs}_g(\cA)\cdot x^{2g}=\kappa(\cA)\cdot\bigl(\hat A(ix)-1\bigr).
\]
Since $\hat A(ix)=(x/2)/\sin(x/2)=1+x^2/24+7x^4/5760+\cdots$, the first
Faber--Pandharipande coefficients are
\[
F_1=\tfrac{\kappa}{24},\qquad F_2=\tfrac{7\kappa}{5760},\qquad F_3=\tfrac{31\kappa}{967680},
\qquad \]
with the general term
$\kappa\cdot\tfrac{2^{2g-1}-1}{2^{2g-1}}\cdot\tfrac{|B_{2g}|}{(2g)!}$.
Each of these is the scalar-lane projection; for multi-weight
families at $g\ge 2$, add $\delta F_g^{\mathrm{cross}}$. Verify
$F_1=\kappa/24$ as sanity check (Cauchy normalization
$1/(2\pi i)$, not $1/(2\pi)$).

The scalar $\kappa(\cA)$ is only the leading term. The bar complex
carries higher-degree data: a universal Maurer--Cartan element
$\Theta_\cA$ whose projection to degree~$r$ yields a shadow invariant
$S_r(\cA)$. Write $\alpha:=S_3$ for the cubic shadow.
On each primary deformation line~$L$ (a one-parameter subfamily
at fixed spin content), the shadow
generating function $H(t)=\sum_{r\ge 2}rS_rt^r$ satisfies the
algebraic relation
\begin{equation}\label{eq:preface-riccati-hook}
H(t)^2=t^4\,Q_L(t),\qquad Q_L(t)=4\kappa^2+12\kappa S_3\,t+(9S_3^2+16\kappa S_4)\,t^2,
\end{equation}
a quadratic polynomial in three genus-$0$ invariants
(Riccati algebraicity theorem, full monograph). The infinite tower is
algebraic of degree~$2$, governed by the discriminant
$\Delta=8\kappa S_4$.

\medskip
\noindent\textbf{Heisenberg: the genus-$1$ partition function.}\enspace
The genus-$1$ Heisenberg partition function on the elliptic curve
$E_\tau=\bC/(\bZ+\bZ\tau)$ is the functional integral over the
free boson. The bar complex computes:
\[
Z_1(\cH_k;\tau)=\frac{1}{\eta(\tau)^k},\qquad\eta(\tau)=q^{1/24}\prod_{n\ge 1}(1-q^n),\quad q=e^{2\pi i\tau}.
\]
The prefactor $q^{1/24}$ in the Dedekind eta is essential for
modular weight $1/2$. The free energy is
$F_1(\cH_k)=-k\log\eta(\tau)$. Expanding:
\[
F_1(\cH_k)=-k\left(\frac{2\pi i\tau}{24}+\sum_{n\ge 1}\log(1-q^n)\right)=\frac{\kappa}{24}\cdot 2\pi i\tau+\text{(instanton corrections)}.
\]
The leading coefficient $\kappa/24=k/24$ matches the $\hat A$-genus
prediction $F_1=\kappa/24$ (with the Cauchy normalization
$1/(2\pi i)$, not $1/(2\pi)$). The instanton corrections
$\sum_{n\ge 1}\log(1-q^n)$ are the genus-$1$ bar complex
contributions from states at conformal weight~$n$; these are
captured by the full Feynman-transform differential, not just the
scalar curvature.

For the rank-$d$ Heisenberg $\cH_k^{\oplus d}$:
$Z_1=1/\eta(\tau)^{dk}$ and $F_1=dk/24\cdot 2\pi i\tau+\cdots$,
consistent with $\kappa(\cH_k^{\oplus d})=dk$.

\medskip
\noindent\textbf{Kac--Moody: the genus-$1$ character.}\enspace
For $\widehat\fg_k$ at genus~$1$, the partition function is the
vacuum character
$\chi_0(\widehat\fg_k;\tau)=\mathrm{tr}_{\cV_k(\fg)}\,q^{L_0-c/24}$.
The Sugawara central charge is $c=k\dim\fg/(k+h^\vee)$, and the
leading asymptotics give
$F_1(\widehat\fg_k)\sim\kappa(\widehat\fg_k)/24\cdot 2\pi i\tau$
with $\kappa=(k+h^\vee)\dim\fg/(2h^\vee)$, matching the
$\hat A$-genus prediction \textsc{(uniform-weight)}.

\medskip
\noindent\textbf{Virasoro: $F_1=c/48$.}\enspace
For the Virasoro algebra at central charge~$c$, the genus-$1$ free
energy is
\[
F_1(\Vir_c)=\frac{\kappa(\Vir_c)}{24}=\frac{c/2}{24}=\frac{c}{48}.
\]
The Virasoro vacuum character on the torus is
$\chi_0(\Vir_c;\tau)=q^{-c/24}/\prod_{n\ge 2}(1-q^n)$; the
leading term $-c/24$ in the exponent gives $F_1=c/48$ after
normalization. This matches: $\hat A(ix)-1=x^2/24+\cdots$, so
$F_1=\kappa/24=(c/2)/24=c/48$.

\medskip
\noindent\textbf{The higher Faber--Pandharipande coefficients.}\enspace
The formula
$F_g=\kappa\cdot\tfrac{2^{2g-1}-1}{2^{2g-1}}\cdot\tfrac{|B_{2g}|}{(2g)!}$
\textsc{(uniform-weight)} involves the Bernoulli numbers $B_{2g}$.
Numerical values:
\begin{center}
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{cccc}
$g$ & $B_{2g}$ & $F_g/\kappa$ & Decimal\\
\hline
$1$ & $1/6$ & $1/24$ & $0.04167$\\
$2$ & $-1/30$ & $7/5760$ & $0.001215$\\
$3$ & $1/42$ & $31/967680$ & $0.00003203$\\
$4$ & $-1/30$ & $127/154828800$ & $8.202\times 10^{-7}$\\
$5$ & $5/66$ & $511/20437401600$ & $2.501\times 10^{-8}$
\end{tabular}
\end{center}
The factorial decay $F_g\sim(2g)!^{-1}$ is \emph{not} the full story:
the factor $2^{2g-1}-1$ grows exponentially, and the Bernoulli numbers
$|B_{2g}|\sim 2(2g)!/(2\pi)^{2g}$ produce a Gevrey-$1$ sequence
$F_g\sim\kappa\cdot(2\pi)^{-2g}$. The shadow obstruction tower sums
these contributions; the Borel summability of the $F_g$ series is
controlled by the shadow growth rate $\rho(\cA)$ (\S6.9).

The shadow obstruction tower is not merely formal. Its projections
yield: the Pixton ideal of the modular curve, the integrable
hierarchies of Gelfand--Dickey type, the Hitchin spectral curve of
the shadow connection, the Baxter $Q$-operator, and the
Bekenstein--Hawking entropy formula of three-dimensional gravity
(twisted holography chapter, full monograph). These are
projections of one object, not separate results.

\subsection*{2.5.\enspace Complementarity}

The genus tower is not merely a sequence of scalar invariants; it
carries a duality structure that pairs each genus-$g$ contribution
of $\cA$ with the corresponding contribution of the Koszul dual
$\cA^!$. This duality is the genus-tower incarnation of Verdier
duality on the Ran space.

Verdier duality on the Ran space splits the center local system into
two halves, one controlled by $\cA$ and one by $\cA^!$, carrying a
shifted-symplectic structure:
\[
R\Gamma(\overline{\mathcal M}_g,\mathcal Z_\cA)\simeq\mathbf Q_g(\cA)\oplus\mathbf Q_g(\cA^!).
\]
What $\cA$ sees as deformation, $\cA^!$ sees as obstruction. The
natural pairing
\[
\mathbf Q_g(\cA)\otimes\mathbf Q_g(\cA^!)\to R\Gamma(\overline{\mathcal M}_g,\omega_{\overline{\mathcal M}_g})\simeq\Bbbk[-(3g-3)]
\]
is a $(-(3g-3))$-shifted symplectic form, and the two summands are
Lagrangian: isotropic of half the total dimension.

\medskip
\noindent\textbf{Heisenberg: complementarity is antisymmetry.}\enspace
For $\cH_k$, the Koszul dual is $\cH_k^!=\Sym^{\mathrm{ch}}(V^*)$
with $\kappa(\cH_k^!)=-k$. The complementarity is
$\kappa(\cH_k)+\kappa(\cH_k^!)=k+(-k)=0$ (Kac--Moody/free-field type).
At genus~$1$: $\mathbf Q_1(\cH_k)$ is one-dimensional (the image of
$\lambda_1$ under the Hodge map), and $\mathbf Q_1(\cH_k^!)$ is
one-dimensional (the complementary image). The shifted symplectic
form on $H^*(\overline{\cM}_{1,1})\cong\bQ^2$ identifies these as
dual lines. The antisymmetry $\kappa'=-\kappa$ means the Koszul dual
sees the opposite curvature: the deformations of $\cH_k$ are the
obstructions of $\cH_k^!$ and conversely.

\medskip
\noindent\textbf{Virasoro: complementarity is asymmetric.}\enspace
For $\Vir_c$, the Koszul dual is $\Vir_{26-c}$ with
$\kappa(\Vir_{26-c})=(26-c)/2$. The complementarity conductor is
$\kappa(\Vir_c)+\kappa(\Vir_{26-c})=c/2+(26-c)/2=13$, which is
nonzero for all $c$. At the self-dual point $c=13$:
$\kappa=\kappa'=13/2$, and the Lagrangian decomposition becomes
an eigenspace decomposition with equal eigenvalues. At $c=26$:
$\kappa=13$, $\kappa'=0$; the dual $\Vir_0$ is uncurved, and all
of the deformation data lies on the $\cA$-side. The nonzero
conductor $13$ is the scalar obstruction to recovering the
genus-$0$ Koszul duality pattern at higher genus.

The scalar sum
rule is family-dependent (never universal):
\[
\kappa(\cA)+\kappa(\cA^!)=\begin{cases}0&\text{(Kac--Moody, free field, lattice)},\\ 13&\text{(Virasoro)},\\ 250/3&(\mathcal W_3),\\ K_N\cdot(H_N-1)&(\mathcal W_N),\end{cases}
\]
where $K_N=c(\mathcal W_N)+c(\mathcal W_N^!)$ is the central-charge
conductor and $H_N=\sum_{j=1}^N 1/j$ the harmonic number.
The scalar $\kappa+\kappa'$ is the kappa-level Koszul conductor;
it is zero for KM and free fields, nonzero for $\mathcal W$-algebras.
Self-dual at $c=13$ for Virasoro, $c=50$ for $\mathcal W_3$; qualify
``self-dual at $c=13$ under Koszul
duality,'' never unqualified.

\subsection*{2.6.\enspace Feigin--Frenkel duality}

The Sugawara field
$T(z)=\tfrac{1}{2(k+h^\vee)}\sum_a{:}J^a(z)J^a(z){:}$
has central charge $c=k\dim\mathfrak g/(k+h^\vee)$. At the critical
level $k=-h^\vee$ the denominator vanishes: $T(z)$ is undefined, not
``$c$ diverges.'' The chiral algebra acquires the Feigin--Frenkel
center $\mathfrak z(\widehat{\mathfrak g}_{-h^\vee})$, isomorphic to
functions on the space of ${}^L\mathfrak g$-opers on the disc.

The Feigin--Frenkel involution $k\leftrightarrow-k-2h^\vee$ is Koszul
duality on configuration spaces: it interchanges $\cA$ and $\cA^!$
while preserving the bar-cobar adjunction. At the critical level, the
Koszul dual is the Langlands-dual critical-level
algebra~$\widehat{{}^L\mathfrak g}_{-{}^Lh^\vee}$, not a renormalised
copy of the original.

\medskip
\noindent\textbf{The Feigin--Frenkel involution in coordinates.}\enspace
For $\fg=\fsl_2$, $h^\vee=2$, and the involution is $k\mapsto -k-4$.
The Koszul dual of $\widehat{\fsl}_{2,k}$ is
$\widehat{\fsl}_{2,-k-4}$. The curvature transforms as
\[
\kappa(\widehat{\fsl}_{2,-k-4})=\frac{3(-k-4+2)}{4}=\frac{-3(k+2)}{4}=-\kappa(\widehat{\fsl}_{2,k}),
\]
confirming the antisymmetry $\kappa+\kappa'=0$ (for affine Kac--Moody). At
$k=-2$ (critical): both $\kappa$ and $\kappa'$ vanish; the bar complex
is uncurved on both sides. At $k=0$ (abelian limit): $\kappa=3/2$,
$\kappa'=-3/2$.

For $\fg=\fsl_N$, $h^\vee=N$, and the involution is $k\mapsto -k-2N$.
The fixed point $k=-N$ is the self-dual level; the Sugawara central
charge at $k=-N$ is $c=(-N)\cdot(N^2-1)/(-N+N)$, which is undefined
(the fixed point of the involution lies at the critical level for
$\fsl_N$). This is not a coincidence: the involution has no fixed
point at generic level, and the critical level is precisely where
duality collapses.

\medskip
\noindent\textbf{The critical level jump.}\enspace
At $k=-h^\vee$, several discontinuities occur simultaneously:
\begin{enumerate}[label=(\roman*)]
\item $\kappa(\widehat\fg_{-h^\vee})=0$: the curvature vanishes, the
bar complex becomes uncurved, and all monodromy becomes trivial
(all KZ exponents become integers).
\item The Sugawara field $T(z)$ is undefined: no conformal vector
exists. The vertex algebra has no Virasoro subalgebra.
\item The center jumps from finite-dimensional to
$\mathfrak z(\widehat\fg_{-h^\vee})\cong\Fun(\Op_{{}^L\fg}(D))$:
the space of ${}^L\fg$-opers on the formal disc.
\item The bar cohomology $H^1(\barB(\widehat\fg_{-h^\vee}))$ doubles
in dimension: for $\fsl_2$, from $4$ (at generic $k$) to $8$ (at
$k=-2$). The extra classes come from the Feigin--Frenkel center.
\item Koszulness fails: the PBW spectral sequence has nontrivial
differentials.
\end{enumerate}
For $\fsl_2$ at $k=-2$: the KZ connection $\nabla_{\KZ}$ has regular
singularities with integer exponents, so all solutions are
single-valued on $\Conf_n(\bP^1)$. The genus spectral sequence has
$d_1=\lambda\cdot[\delta]$ (where $\lambda=(k+h^\vee)$ is the shifted
level); at $\lambda=0$ this differential vanishes, and the $E_1$ page
does not degenerate.

\subsection*{2.7.\enspace The total space}

The universal configuration fibration
$\pi_n\colon\overline{\mathcal C}_n(\mathcal C_g)\to\overline{\mathcal M}_g$
packages the bar complex into a single global object. Its boundary
divisors carry two distinct geometric roles. \emph{Collision
divisors} (vertical): the fibrewise boundary of
$\overline{\mathrm{FM}}_n(X_s)$, producing the bar differential
$d_{\mathrm{res}}$ (OPE residues). \emph{Degeneration divisors}
(horizontal): the boundary of $\overline{\mathcal M}_g$ itself (nodal
curves), producing the period corrections and Gauss--Manin terms.

Algebraic boundary (Borcherds) meets geometric boundary (period map
and clutching). Their interaction is the curvature~$\kappa$: the
fibrewise bar differential fails to be nilpotent precisely because
the vertical and horizontal boundaries do not commute.

\subsection*{2.8.\enspace The $E_n$ hierarchy and the genus tower}

The curvature $d_{\mathrm{fib}}^2=\kappa\cdot\omega_g$ is a statement
about the $E_\infty$-chiral bar complex. At the $E_1$ (ordered)
level, the same curvature appears but the additional structure of the
$R$-matrix produces genus-dependent corrections invisible to the
symmetric bar.

\medskip
\noindent\textbf{$E_\infty$-chiral (standard VAs): the curvature is
scalar.}\enspace
For any $E_\infty$-chiral algebra (all standard VAs:
Heisenberg, Kac--Moody, Virasoro, $\cW_N$, $\beta\gamma$, lattice),
the symmetric bar complex $\barB^\Sigma(\cA)$ is a coalgebra on
the Ran space $\Ran(X)$ (unordered configurations). The curvature
$d_{\mathrm{fib}}^2=\kappa\cdot\omega_g$ is a scalar multiple of
the Hodge class: the $\Sigma_n$-averaging has projected out all
non-scalar data. The genus tower is controlled by $\kappa$ alone
\textsc{(uniform-weight)}.

\medskip
\noindent\textbf{$E_1$-chiral (Yangians): the curvature carries
$R$-matrix corrections.}\enspace
For a genuinely $E_1$-chiral algebra (e.g., a chiral Yangian
$Y(\fg)^{\mathrm{ch}}$), the ordered bar
$\barB^{\mathrm{ord}}(\cA)$ is a coalgebra on ordered
configurations $\Conf_n^{\mathrm{ord}}(X)$. The curvature
$d_{\mathrm{fib}}^2$ at genus~$g$ is \emph{not} scalar: it
carries $R$-matrix corrections from the ordering. The genus-$1$
curvature for $Y(\fg)^{\mathrm{ch}}$ involves the elliptic
$R$-matrix (the KZB $R$-matrix on the torus), which is a function
of the spectral parameter $z$ and the modular parameter $\tau$.
The genus tower for $E_1$-chiral algebras carries strictly more
data than the symmetric bar: the KZB connection, the elliptic
monodromy, and the Drinfeld--Kohno relations.

\medskip
\noindent\textbf{The derived chiral centre and the $E_n$ output.}\enspace
The bar complex $\barB(\cA)$ is an $E_1$-chiral coassociative
coalgebra (differential plus deconcatenation coproduct). It does
\emph{not} carry $\SCchtop$ structure. The $\SCchtop$ structure
(Swiss-cheese: two colours, bulk and boundary) emerges on the
\emph{derived chiral centre}
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)=\ChirHoch^*(\cA,\cA)$,
computed using the bar complex as a resolution:
\[
\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)=R\Hom_{\cA\text{-bimod}}(\cA,\cA)\simeq\Hom(\barB(\cA),\cA).
\]
The pair $(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA),\cA)$ is the
$\SCchtop$-datum: $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ is the
bulk (closed colour), $\cA$ is the boundary (open colour), and the
action of the bulk on the boundary is by chiral Hochschild evaluation.

For $E_\infty$-chiral input: Theorem~H gives
$\ChirHoch^*(\cA)\in\{0,1,2\}$ (concentrated, polynomial Hilbert
series). With conformal vector at non-critical level (Sugawara):
$\SCchtop+\text{conformal vector}=E_3$-topological;
the conformal vector kills the chiral direction. Proved for affine
KM at non-critical level; conjectural for general chiral algebras
with conformal vector.

For $E_1$-chiral input (Yangians): the symmetric bar $\barB^\Sigma$
does not exist (the D-module does not descend to symmetric
configurations). The derived centre gives $E_2$ only (via classical
Deligne, not Higher Deligne), and the passage to $E_3$ requires the
Drinfeld centre construction.

\subsection*{2.9.\enspace Bar chain models on curve geometries}

The bar complex changes character as the underlying geometry changes.
Three geometric inputs produce three different bar models, each
carrying progressively richer structure:

\medskip
\noindent\textbf{Over the formal disc $D=\Spec\bC[[z]]$:}\enspace
The bar complex $\barB(\cA|_D)=(T^c(s^{-1}\bar\cA),d_B)$ is the
classical bar construction with deconcatenation coproduct. The
propagator is $d\log z$, the Arnold relation is trivial (one variable),
and $d_B^2=0$ unconditionally. The bar cohomology
$H^*(\barB(\cA|_D))$ is the Koszul dual in the classical sense.
Restricting to $D$ recovers the formal-disk Koszul duality of
Beilinson--Ginzburg--Soergel; the passage $D\to X$ adds
configuration-space geometry.

\medskip
\noindent\textbf{Over the affine line $\bA^1$:}\enspace
The bar complex $\barB(\cA|_{\bA^1})$ uses the propagator
$d\log(z_1-z_2)$ on ordered configurations $\Conf_n(\bA^1)$.
The Arnold relation $\eta_{12}\wedge\eta_{23}+\text{cyc}=0$ is
nontrivial and provides the codimension-two cancellation
$d_B^2=0$. The FM compactification
$\overline{\FM}_n(\bA^1)$ is the real Stasheff associahedron
$K_n$; its chain complex $C_*(K_n)$ carries the $A_\infty$-operad.
The ordered bar on $\bA^1$ produces the $A_\infty$-structure on
$H^*(\barB(\cA))$: the transferred operations $m_n$ are the
Stasheff products, computed by integrating $\eta_{ij}$ over the
faces of $K_n$.

\medskip
\noindent\textbf{Over a compact curve $X$ of genus~$g$:}\enspace
The bar complex $\barB^{(g)}(\cA)$ uses the genus-$g$ propagator
$\eta^{(g)}_{12}=d\log E(z_1,z_2)+\text{(period correction)}$.
The Arnold relation acquires a $(1,1)$-defect proportional to
$\omega_g$, producing the curvature $d_{\mathrm{fib}}^2=\kappa\cdot\omega_g$.
The configuration space $\Conf_n(X)$ compactifies to
$\overline{\FM}_n(X)$ (smooth, with normal-crossings boundary), and
the chain complex $C_*(\overline{\FM}_n(X))$ carries the operadic
structure of $C_*(\overline{\cM}_{0,n+1})$ plus higher-genus
corrections from the period matrix. The bar complex over $X$ sees
the Hodge bundle $\mathbb E$, the clutching morphisms, and the
planted-forest strata of Mok's compactification.

\medskip
\noindent\textbf{The chain of refinements.}\enspace
The passage from $D$ to $\bA^1$ to $X$ is a chain of geometric
refinements, each introducing new structure:
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{llll}
\textbf{Space} & \textbf{Propagator} & \textbf{New feature} & \textbf{Bar model}\\
\hline
Formal disc $D$ & $d\log z$ & none & classical bar\\
Affine line $\bA^1$ & $d\log(z_1{-}z_2)$ & Arnold relation & $A_\infty$-bar\\
Smooth curve $X_g$ & $d\log E+\text{period}$ & curvature $\kappa\cdot\omega_g$ & modular bar\\
Nodal curve $X_0$ & degenerate limit & clutching morphisms & Feynman transform\\
Universal family $\cC_g$ & fibred propagator & Gauss--Manin & total bar $D_\cA$
\end{tabular}
\end{center}
No step in this chain is trivial. The passage $D\to\bA^1$ already
introduces configuration-space topology, FM compactifications, and
the $E_1/E_\infty$ distinction. The passage $\bA^1\to X$ adds
curvature from the Hodge bundle. The passage to nodal curves adds
clutching from boundary strata. The passage to the universal family
assembles everything into the total differential $D_\cA$ with
$D_\cA^2=0$.


% ====================================================================
\section*{3.\quad Modular homotopy theory}
% ====================================================================

The genus tower demands an organising framework. The fibrewise
differential, the Gauss--Manin correction, and the clutching morphisms
at boundary strata satisfy compatibility relations dictated by the
stratification of $\overline{\cM}_{g,n}$. The governing algebraic
structure is the \emph{modular operad}: an operad whose operations are
indexed by connected stable graphs of arbitrary genus.

The \emph{modular homotopy type} of $\cA$ is the formal moduli problem
classifying the inverse system of bar complexes,
\[
\mathcal M^{\mathrm{mod}}_\cA(R):=\operatorname{MC}(\mathfrak g^{\mathrm{mod}}_\cA\widehat\otimes_{\mathfrak m}R)/{\sim}
\]
for local Artin rings~$R$. Here $\mathfrak g^{\mathrm{mod}}_\cA$ is
the \emph{modular convolution algebra}: a complete filtered cyclic
$L_\infty$-algebra. Three inputs enter: a homotopy chiral algebra on
the curve, a cooperadic chain complex on logarithmic configuration
spaces, and a convolution $L_\infty$-structure mediating between them.
The bar complex, the Koszul dual, the genus tower, the
complementarity splitting, and the shadow obstruction tower are all
representations of $\mathcal M^{\mathrm{mod}}_\cA$.

The primitive story lives on ordered configurations. The $E_1$
convolution algebra $\mathfrak g^{\mathrm{mod},E_1}_\cA$, built on
ribbon graphs from $F\!\Ass$, is the primary object; the modular
convolution algebra $\gAmod$ is its image under the av map from
ordered to symmetric. Every construction in this section begins with
the $E_1$ structure and descends.

\subsection*{3.1.\enspace The modular operad}

At genus~$0$, the combinatorics is governed by trees; at higher
genus, by stable graphs with genus labels at their vertices. A
\emph{modular operad} (Getzler--Kapranov~\cite{GeK98}) has operations
indexed by connected stable graphs. A \emph{connected stable graph}
$\Gamma$ has a label $g(v)\in\mathbb Z_{\ge 0}$ at each vertex
satisfying $2g(v)-2+\operatorname{val}(v)>0$ and total genus
$g(\Gamma)=b_1(\Gamma)+\sum_v g(v)$; trees are the genus-$0$ case.
The structure maps are \emph{separating gluing}
$\xi_{\mathrm{sep}}\colon\cO(g_1,n_1{+}1)\otimes\cO(g_2,n_2{+}1)\to\cO(g_1{+}g_2,n_1{+}n_2)$
and \emph{non-separating gluing}
$\xi_{\mathrm{ns}}\colon\cO(g,n{+}2)\to\cO(g{+}1,n)$.

A stable graph records a degeneration of a smooth curve into a nodal
curve: vertices are irreducible components, edges are nodes, genus
labels are component genera, half-edges are marked points. The set
$\mathsf{Gr}^{\mathrm{st}}_{g,n}$ parametrises the boundary
stratification of $\overline{\cM}_{g,n}$. Every codimension-one
boundary divisor is a one-edge degeneration; every codimension-two
stratum is the intersection of exactly two codimension-one divisors,
appearing with opposite orientations.

\medskip
\noindent\textbf{Stable graph counts.}\enspace
The number of stable graph types grows with genus and marked points.
At genus~$1$: $\overline{\cM}_{1,1}$ has one boundary divisor
$\delta_{\mathrm{irr}}$ (the single self-loop graph with one
genus-$0$ vertex and one non-separating edge).
$\overline{\cM}_{1,2}$ has three boundary divisors: one
non-separating ($\delta_{\mathrm{irr}}$, the self-loop with two
external legs at the same vertex) and two separating ($\delta_0$,
splitting into a genus-$1$ vertex with one leg and a genus-$0$
vertex with two legs; counted once for each labeling).
At genus~$2$:
$\overline{\cM}_{2,0}$ has $3$ boundary divisors (the figure-eight
self-loop, the separating barbell, and the sunset/banana graph);
$\overline{\cM}_{2,1}$ has $7$ boundary strata including codimension-two
intersections. The count of stable graph types at genus $g$ with $n$
marked points is the number of cells in the orbicell decomposition
of $\overline{\cM}_{g,n}$, which grows polynomially in $n$ at fixed
$g$ and exponentially in $g$ at fixed~$n$.

\medskip
\noindent\textbf{The $E_1$ modular operad: ribbon graphs.}\enspace
The $E_1$-primitive version uses the Feynman transform of $\Ass$:
the operations are indexed by \emph{ribbon graphs} (fatgraphs),
connected graphs with a cyclic ordering of the half-edges at each
vertex. A ribbon graph $\Gamma$ determines a compact surface with
boundary by thickening each vertex to a polygon and each edge to a
ribbon. The genus is $g(\Gamma)=(2-|V|+|E|-|F|)/2$ where $F$ counts
the boundary components. Ribbon graphs are the combinatorial model of
$\overline{\cM}_{g,n}$ via the Harer--Mumford--Penner cell
decomposition: each top cell corresponds to a trivalent ribbon graph,
and the cell complex computes $H_*(\cM_{g,n})$.

The coinvariant map $\mathrm{av}\colon F\!\Ass\to F\Com$ forgets the
cyclic ordering. At each vertex, the $|\mathrm{val}(v)|!$ orderings
of incoming half-edges are identified; the resulting Euler
characteristic is the count of unordered stable graphs, weighted by
$1/|\Aut(\Gamma)|$. This projection is lossy: the $R$-matrix
data at each vertex, which requires an ordering of inputs, is
destroyed.

The Feynman transform replaces trees by stable graphs,
\begin{equation}\label{eq:preface-feynman-sum}
F\cO(g,n)=\bigoplus_{\Gamma\in\mathsf{Gr}^{\mathrm{st}}_{g,n}}\frac{\hbar^{g(\Gamma)}}{|\operatorname{Aut}(\Gamma)|}\bigotimes_{v\in V(\Gamma)}\cO\bigl(g(v),\operatorname{In}(v)\bigr).
\end{equation}

\subsection*{3.2.\enspace The Feynman transform differential}

The differential contracts one edge at a time,
\[
d_{F\cO}(\gamma_\Gamma)=\sum_{e\in E(\Gamma)}(-1)^{\epsilon(e)}\xi_e(\gamma_{\Gamma/e}),
\]
with the sign from the position of $e$ in the ordering on $E(\Gamma)$
recorded by $\det(E(\Gamma))$. The identity $d^2=0$ is the
codimension-$2$ cancellation: each pair of edges contracts in either
order, and the two terms cancel by associativity of~$\cO$. At
genus~$0$, $F\cO$ reduces to the operadic bar construction.

When $\cO=\Com$, each vertex factor in~\eqref{eq:preface-feynman-sum}
is one-dimensional, and the Feynman transform becomes the stable
graph complex
\[
F\Com(g,n)=\bigoplus_{\Gamma\in\mathsf{Gr}^{\mathrm{st}}_{g,n}}\frac{\hbar^{g(\Gamma)}}{|\operatorname{Aut}(\Gamma)|}\det(E(\Gamma)).
\]
When $\cO=\Ass$, the Feynman transform $F\!\Ass$ sums over ribbon
graphs (fatgraphs); this is the $E_1$-primitive input for the ordered
convolution algebra.

\medskip
\noindent\textbf{Explicit graph computation: genus~$1$, $n=1$.}\enspace
At $(g,n)=(1,1)$, there is a single stable graph type: the graph
$\Gamma_{\mathrm{irr}}$ with one vertex of genus~$0$, one external
half-edge (the marked point), and one internal edge forming a
self-loop. The genus formula: $g(\Gamma)=b_1(\Gamma)+g(v)=1+0=1$.
The stability condition: $2g(v)-2+\mathrm{val}(v)=0-2+3=1>0$
(the vertex has valence $3$: one external half-edge plus two
half-edges of the self-loop). The automorphism group has order $2$
(swapping the two half-edges of the self-loop). The Feynman transform
gives:
\[
F\Com(1,1)=\frac{\hbar}{2}\cdot\Com(0,3)\otimes\det(\Bbbk\cdot e)=\frac{\hbar}{2}\cdot\Bbbk\otimes\Bbbk.
\]
The differential from $(1,1)$: contracting the self-loop sends
$\Gamma_{\mathrm{irr}}$ to the corolla $(1,1)$ (a single genus-$1$
vertex with one external leg). The differential computes:
$d_{F\Com}(\gamma_{\Gamma_{\mathrm{irr}}})=\pm\xi_{\mathrm{ns}}(\gamma)$.

\medskip
\noindent\textbf{Explicit graph computation: genus~$2$, $n=0$.}\enspace
At $(g,n)=(2,0)$, there are $3$ stable graph types:
\begin{enumerate}[label=(\alph*)]
\item The \emph{figure-eight} $\Gamma_8$: one genus-$0$ vertex with
two self-loops. $b_1=2$, $g(v)=0$, $\mathrm{val}(v)=4$, stability
$0-2+4=2>0$. $|\Aut|=8$ (swap each loop $\times$ swap the two loops:
$2\times 2\times 2$).
\item The \emph{sunset} (banana) $\Gamma_{\mathrm{sun}}$: two
genus-$0$ vertices connected by three edges. $b_1=2$, $g(v_1)=g(v_2)=0$,
$\mathrm{val}=3$ at each vertex, stability $0-2+3=1>0$ at each.
$|\Aut|=12$ ($S_3$ permuting three edges $\times$ $\bZ/2$ swapping
the two vertices).
\item The \emph{separating barbell} $\Gamma_{\mathrm{bar}}$: two
genus-$1$ vertices connected by one edge. $b_1=0$, $g(v_1)=g(v_2)=1$,
total $g=0+1+1=2$. $\mathrm{val}=1$ at each, stability
$2-2+1=1>0$. $|\Aut|=2$ (swapping the two vertices).
\end{enumerate}
These three types exhaust $\mathsf{Gr}^{\mathrm{st}}_{2,0}$; no other
connected stable graph of genus~$2$ with $0$ marked points exists.
The three types correspond to the three boundary divisors of
$\overline{\cM}_2$: $\delta_0$ (irreducible, the figure-eight and
sunset), $\delta_1$ (the separating barbell).

\subsection*{3.3.\enspace The convolution ladder}

At each level of generality, the bar-type construction is a
convolution dg Lie algebra whose Maurer--Cartan elements classify
algebraic structures:
\begin{equation}\label{eq:preface-convolution-ladder}
\begin{array}{r@{\;:\quad}c@{\qquad}l}
\text{algebra} & \Hom(B(\Ass),\End_A) & A_\infty\text{-structures on }A\\[3pt]
\text{operad} & \Hom_\Sigma(B(\cP),\End_V) & \cP_\infty\text{-structures on }V\\[3pt]
\text{modular} & \Hom_\Sigma(F\cO,\End_{\barB(\cA)}) & \text{consistent genus towers}
\end{array}
\end{equation}
The first line is topological Hochschild; the second is the Ginzburg--Kapranov
deformation complex; the third governs this book. The Lie bracket is
the convolution bracket
\[
[f,g]=\mu\circ(f\otimes g)\circ\Delta-(-1)^{|f||g|}\mu\circ(g\otimes f)\circ\Delta,
\]
with $\Delta$ the cooperadic decomposition and $\mu$ the operadic
composition.

The \emph{primitive $E_1$ convolution}
\[
\mathfrak g^{\mathrm{mod},E_1}_\cA:=\Hom_\Sigma\bigl(F\!\Ass,\End_{\barB^{E_1}(\cA)}\bigr)
\]
is the ordered, ribbon-graph input: the algebraic form of the 't~Hooft
$1/N$ expansion. Setting $\hbar=1/N^2$, the MC element
$\Theta^{E_1}_\cA\in\operatorname{MC}(\mathfrak g^{\mathrm{mod},E_1}_\cA)$
is the genus expansion $\sum_g N^{2-2g}F_g(\lambda)$ summed over
ribbon graphs weighted by the genus of their embedding surface.
Planar ($g=0$) diagrams dominate at large~$N$; the shadow obstruction
tower $\Theta^{E_1,\le r}$ is the truncation to $r$-point 't~Hooft
interactions.

The \emph{modular convolution algebra} is the av-image,
\begin{equation}\label{eq:preface-gmod}
\gAmod:=\Hom_\Sigma\bigl(F\Com,\End_{\barB(\cA)}\bigr).
\end{equation}
The coinvariant map $F\!\Ass\to F\Com$ projects
$\Theta^{E_1}\mapsto\Theta$: colour-ordered amplitudes to full
amplitudes. On each primary line, the shadow tower is algebraic of
degree~$2$: the entire infinite sequence is the Taylor expansion of
$\sqrt{Q_L}$ for a single quadratic $Q_L$, the shadow metric
(\S6 below).

\medskip
\noindent\textbf{Heisenberg: the convolution algebra is
abelian.}\enspace For $\cH_k$, the modular convolution algebra
$\gAmod[\cH_k]$ is abelian: $[f,g] = 0$ for all $f,g$. The
bracket vanishes because the only nonzero amplitude is
$\Phi_{\Gamma_2} = k$ (single-edge graph), and
$\Delta(\Gamma_2)$ has no non-trivial splitting. Hence
$\Theta_{\cH_k} = k \cdot \eta \otimes \Lambda$ is the unique
MC element (no gauge freedom, no moduli). The genus tower is
determined entirely by the graph enumeration of $F\Com$: for
the Heisenberg, the bar construction reduces to the
combinatorics of stable graphs weighted by a single scalar.

\noindent\textbf{Kac--Moody: the bracket is the Lie algebra.}\enspace
For $\widehat{\fg}_k$, the degree-$3$ convolution bracket
$\ell_2(\Theta, \Theta)$ encodes the Lie bracket $[\cdot,\cdot]$
of $\fg$ through the cubic shadow $S_3 = 2h^\vee/(3\kappa)$.
The Jacobi identity $[[\cdot,\cdot],\cdot] + \text{cyc} = 0$
kills the degree-$4$ shadow: $S_4 = 0$, $\Delta = 0$, and the
tower terminates. The convolution algebra of $\widehat{\fg}_k$
is a non-abelian Lie algebra at degree~$3$ that becomes abelian
at degree~$4$ by Jacobi. Class~$\mathbf{L}$: Lie structure
controls and then terminates the tower.

\medskip
\noindent\textbf{Remark} (Homotopy types in three stages). The three
levels of the convolution ladder mirror three levels of homotopy
theory. \emph{Over a field} (the bar complex of a graded algebra):
$B(A)=(T^c(s^{-1}\bar A),d_B)$ determines
the homotopy type of an associative algebra; formality corresponds to
intrinsic formality; Massey products measure the obstruction.
\emph{Over a manifold}: the Sullivan minimal model $(\Lambda V,d)$
determines the rational homotopy type; K\"ahler manifolds are formal.
The Heisenberg algebra is the vertex-algebraic analogue: its shadow
obstruction tower terminates at degree~$2$, the Gaussian archetype.
\emph{Over a curve at all genera}: the $A_\infty$-products $m_k$ of
the first stage become the modular $L_\infty$-brackets $\ell_k^{(g)}$;
formality becomes the Gaussian archetype; the shadow obstruction tower
is the modular Massey product tower. The shadow depth classification
(\S6) makes this analogy precise: the four classes G, L, C, M
correspond to four levels of modular formality.

\medskip
\noindent\textbf{Virasoro: the convolution algebra is infinite-dimensional.}\enspace
For $\Vir_c$, the convolution bracket
$\ell_2(\Theta,\Theta)$ produces a nonzero cubic shadow from the
simple-pole OPE $T(z)T(w)\sim 2T(w)/(z-w)^2+\cdots$. But the
bar cohomology $H^*(\barB(\Vir_c))$ is one-dimensional in each degree:
spanned by the class $x^r$ (the $r$-th symmetric power of the
dual to~$T$). The convolution bracket $[\cdot,\cdot]$ on
$\gAmod[\Vir_c]$ is \emph{not} a Lie algebra (it violates Jacobi at
degree~$4$, where the quartic shadow $S_4\neq 0$). Instead, the
convolution algebra carries the full $L_\infty$ structure with all
higher brackets $\ell_k$ nonvanishing; the MC equation
$D\Theta+\tfrac{1}{2}[\Theta,\Theta]=0$ holds in the
\emph{$L_\infty$ sense}, not the strict Lie sense. The shadow
obstruction tower for Virasoro is governed by this $L_\infty$
structure: the depth-$\infty$ property is a direct reflection of the
infinite sequence of nontrivial $L_\infty$ brackets.

\medskip
\noindent\textbf{Koszulness as central question.}\enspace
Within this formality classification, the Koszulness property is the
central organizing question of the programme. A chiral algebra is
\emph{chirally Koszul} iff its bar cohomology concentrates in
diagonal degrees and the cobar-bar counit
$\Omega(\barB(\cA))\to\cA$ is a quasi-isomorphism. Twelve equivalent
conditions (ten unconditional, one conditional on perfectness, one
one-directional) characterise this locus. The Koszulness programme
(\S9) proves the core equivalences from PBW concentration, bar-cobar
inversion, chiral Hochschild polynomial growth, and Koszul-complex
acyclicity. All standard families are Koszul; shadow depth classifies
the complexity of Koszul algebras, not Koszulness itself.

\medskip
\noindent\textbf{The twelve Koszul equivalences (overview).}\enspace
The characterisation of chirally Koszul algebras involves twelve
conditions, of which ten are unconditional:
\begin{enumerate}[label=(\roman*)]
\item Bar cohomology concentrates on the diagonal (PBW).
\item The cobar-bar counit is a quasi-isomorphism (inversion).
\item The Koszul complex is acyclic.
\item The chiral Hochschild cohomology $\ChirHoch^*(\cA)$ has
polynomial Hilbert series, concentrated in degrees $\{0,1,2\}$.
\item The bar Hilbert series $h_{\cA^!}(q)$ is rational (holonomic).
\item The spectral discriminant $\Delta_\cA(t)$ is a polynomial.
\item The genus expansion $F_g=\kappa\cdot\lambda_g^{\mathrm{FP}}$
holds at all genera \textsc{(uniform-weight)};
for multi-weight: $F_g=\kappa\cdot\lambda_g+\delta F_g^{\mathrm{cross}}$
at genus~$0$ only.
\item $\ChirHoch^*(\cA)$ is a free polynomial algebra (conditional
on Massey vanishing from FM formality).
\item The vertex algebra admits an $E_\infty$-chiral structure
compatible with the bar filtration.
\item The Koszul dual $\cA^!$ is well-defined as a strict chiral algebra.
\end{enumerate}
Equivalences (i)$\Leftrightarrow$(ii)$\Leftrightarrow$(iii) are
classical (Priddy, Beilinson--Ginzburg--Soergel); their chiral
extensions are Theorem~B. Equivalences
(iv)$\Leftrightarrow$(v)$\Leftrightarrow$(vi) are Theorem~H.
Equivalence (vii) is Theorem~D (genus~$1$ unconditional for
all families; uniform-weight at all genera via
clutching/GRR; multi-weight $g \ge 2$ with explicit
cross-channel correction).

\subsection*{3.4.\enspace Homotopy chiral algebras}

The convolution algebra requires a cochain-level algebraic input, not
merely the cohomology-level chiral bracket. The \v Cech totalisation
provides this: it replaces the strict chiral algebra with a
homotopy-coherent model carrying all derived OPE data.

Fix an affine cover $\mathfrak U=\{U_\alpha\}$ of~$X$. The \v Cech
totalisation
\[
A^{\mathrm{ch}}_\infty:=\check C^\bullet(\mathfrak U;\cA)=\bigoplus_{p\ge 0}\prod_{\alpha_0<\cdots<\alpha_p}\cA(U_{\alpha_0}\cap\cdots\cap U_{\alpha_p})
\]
carries a $\mathrm{Ch}_\infty$-algebra structure (Malikov--Schechtman):
the chiral bracket restricted to overlaps satisfies Jacobi up to a
coherent system of higher homotopies, the \emph{secondary Borcherds
operations}
\[
F_n\colon\operatorname{Lie}(n)\otimes\cY(n)\to P_n(\{A^{\mathrm{ch}}_\infty\},A^{\mathrm{ch}}_\infty),\qquad n\ge 2,
\]
encoding derived OPE data at all pole orders. $F_2$ is the chiral
bracket; $F_3$ is the Jacobiator homotopy arising from
$\overline{\mathcal M}_{0,4}\cong\mathbb P^1$, whose boundary has
three points corresponding to OPE compositions
$(a_{(m)}b)_{(n)}c$ and cyclic permutations. Higher operations $F_n$
are determined inductively by $C_*(\overline{\mathcal M}_{0,n+1})$;
the transferred operations are the associahedral $A_\infty$-corrections.

Different affine covers yield quasi-isomorphic $\mathrm{Ch}_\infty$-algebras.
The strict chiral algebra $\cA$ is the $H^0$ of this structure: the
primitive local object is the homotopy chiral algebra, and the strict
algebra appears after rectification. Vallette rectification: the
homotopy category of $\mathrm{Ch}_\infty$-algebras is equivalent to
the homotopy category of strict chiral algebras, via the bar-cobar
adjunction.

\medskip
\noindent\textbf{Heisenberg: the $A_\infty$ model is strict.}\enspace
For $\cH_k$, the OPE is purely quadratic
($J(z)J(w)\sim k/(z-w)^2$), so all transferred operations $F_n$
with $n\ge 3$ vanish: the Jacobiator homotopy $F_3=0$ (there is no
Jacobi identity to correct for a single generator with no simple
pole), and all higher homotopies vanish. The $\mathrm{Ch}_\infty$-model
is \emph{strict}: $A_\infty^{\mathrm{ch}}(\cH_k)=\cH_k$ with
$m_2=\mu$ (the chiral product) and $m_n=0$ for $n\ge 3$. This
strictness reflects the Gaussian archetype: the bar complex
$\barB(\cH_k)=(T^c(s^{-1}\bar\cH_k),d_B)$ has $d_B$ determined
entirely by $m_2$, with no higher corrections.

\medskip
\noindent\textbf{Kac--Moody: a single nontrivial homotopy.}\enspace
For $\widehat\fg_k$, the OPE has both a double pole
($J^a(z)J^b(w)\sim k(a,b)/(z-w)^2$) and a simple pole
($J^a(z)J^b(w)\sim [a,b](w)/(z-w)$). The Jacobiator homotopy
$F_3$ is nontrivial: it corrects the failure of strict Jacobi in
the \v Cech model. However, $F_4=0$ (and all higher $F_n=0$)
because the Jacobi identity for $\fg$ forces the higher
obstruction classes to be exact. The $A_\infty$-model has
$m_2$ (the chiral bracket), $m_3$ (the Jacobiator homotopy),
and $m_n=0$ for $n\ge 4$. This reflects the class-L structure:
the shadow obstruction tower terminates at degree~$3$.

\medskip
\noindent\textbf{Virasoro: all homotopies nonvanishing.}\enspace
For $\Vir_c$, the Jacobiator homotopy $F_3\neq 0$
(from the quartic OPE pole, after $d\log$ absorption), the
quaternary homotopy $F_4\neq 0$ (from the failure of the Jacobi
identity at the quartic level), and all higher $F_n\neq 0$ by
induction (the quintic forcing of \S6.9 generates nonvanishing
homotopies at every order). The $A_\infty$-model has all $m_n\neq 0$:
this is the class-M structure, the infinite $A_\infty$-depth.

\subsection*{3.5.\enspace Logarithmic Fulton--MacPherson spaces}

The classical FM compactification records collisions on a smooth
variety. Its logarithmic extension (Mok) records collisions along a
divisor and provides the normal-crossings boundary structure on which
$D^2=0$ depends.

For a simple-normal-crossing pair $(X,D)$, Mok constructs
$\mathrm{FM}_n(X|D)$: a smooth variety with corners compactifying
$\mathrm{Conf}_n(X\setminus D)$, with boundary stratification indexed
by \emph{rigid planted-forest types}. A planted-forest type $\rho$
consists of a partition of $\{1,\ldots,n\}$ into blocks (the roots),
a rooted tree per block recording the hierarchy of collisions, and a
grid-depth assignment $w_v\in\mathbb Z_{\ge 0}$ at each vertex
recording the order of tangency with~$D$. The ordinary FM is the
case $D=\emptyset$.

The \emph{degeneration formula}: for a semistable $W\to B$ with
singular fibre $W_0=\bigcup Y_v$ and a rigid type $\rho$,
\[
\mathrm{FM}_n(W/B)(\rho)\longrightarrow\prod_{v\in V(S_\rho)}\mathrm{FM}_{I_v}(Y_v|D_v)
\]
is a proper birational correspondence factoring the global FM
geometry into a fibre product of local pieces. Tropicalisation:
$\operatorname{Trop}(\mathrm{FM}_n(\mathbb C|D))=G_{\mathrm{pf}}$, the
planted-forest poset with grafting as partial order. The planted
forest poset is the combinatorial skeleton of the geometric input,
just as the stable graph complex is the skeleton of the Feynman
transform.

The \emph{Mok codimension formula}: for a type with grid depths
$(w_1,\ldots,w_r)$ and tree vertex counts $(|V(T_j)|)_{j=1,\ldots,s}$,
\[
\operatorname{codim}(W_\rho)=\sum_{i=1}^r w_i+\sum_{j=1}^s(|V(T_j)|-1).
\]
For $\mathrm{FM}_3$: four codimension-one strata ($\{12\}$, $\{23\}$,
$\{13\}$, $\{123\}$), three codimension-two strata
($\{12{<}123\}$, $\{23{<}123\}$, $\{13{<}123\}$).

The chain complexes $\cC^{\log\mathrm{FM}}_{X|D}(n):=C_\bullet(\mathrm{FM}_n(X|D))$
carry cooperadic structure: the inclusion of boundary strata defines
cocomposition maps. For a rigid stable graph~$\Gamma$,
\[
\Delta^{\log}_\Gamma:=(\nu_\Gamma)_*\circ\operatorname{Res}_{D^{\log}_\Gamma}\colon\cC^{\log\mathrm{FM}}_{\mathrm{mod}}(g,n)\to\bigotimes_{v\in V(\Gamma)}\cC^{\log\mathrm{FM}}_{\mathrm{mod}}\bigl(g(v),I_v\sqcup H(v)\bigr)[-|E_{\mathrm{int}}(\Gamma)|],
\]
where $\nu_\Gamma$ is the Mok birational correspondence and
$\operatorname{Res}_{D^{\log}_\Gamma}$ is the residue along the
logarithmic boundary divisor.

\subsection*{3.6.\enspace The convolution $L_\infty$-algebra}

The cooperadic and operadic inputs of \S\S3.4--3.5 must be coupled.
The coupling datum is a twisting morphism: a linear map satisfying a
Maurer--Cartan equation in the convolution complex.

A twisting morphism $\alpha\colon\cC\to\cP$ (satisfying
$\partial\alpha+\alpha\star\alpha=0$) determines a convolution
$sL_\infty$-algebra $\operatorname{hom}_\alpha(\cC,\cP)$
(Robert-Nicoud--Wierstra, after Vallette) with underlying space
$\prod_{n\ge 1}\Hom_{\Sigma_n}(\cC(n),\cP(n))$. The brackets
\[
\ell_k(f_1,\ldots,f_k)(x)=\sum\gamma_\cP\bigl((\alpha\circ 1)(f_1\otimes\cdots\otimes f_k)\Delta^{(k)}_\cC(x)\bigr)
\]
come from iterated cooperadic decomposition. $\ell_1$ is the
convolution differential; $\ell_2$ is the Lie bracket of
coderivations; higher $\ell_k$, $k\ge 3$, arise whenever $\cC$ is not
concentrated in a single degree.

The $sL_\infty$-algebra extends to $\infty$-morphisms in either slot
separately but not both simultaneously: the convolution is
functorial in each slot, but does not assemble into a bifunctor. The
MC3 categorical lift proceeds one slot at a time. The bar-cobar
adjunction is a Quillen equivalence (Vallette); different
$\mathrm{Ch}_\infty$ presentations yield quasi-isomorphic
deformation theories.

\medskip
\noindent\textbf{The three pillar constraints.}\enspace
Three structural limitations govern the convolution construction:
\begin{enumerate}[label=(\roman*)]
\item The convolution $sL_\infty$-algebra
$\operatorname{hom}_\alpha(\cC,\cA)$ is \emph{not} strict Lie (it
carries higher brackets $\ell_k$ for $k\ge 3$). The strict chart
$\Convstr$ is a strict Lie algebra with the same MC moduli, but it
is a chart, not the full structure: transfer and formality require
the $L_\infty$-data.
\item The convolution $\operatorname{hom}_\alpha$ is functorial in
each slot by $\infty$-morphisms, but fails as a \emph{bifunctor}: one
cannot simultaneously vary both the cooperadic and operadic inputs.
The MC3 categorical lift (thick generation of the homotopy category)
proceeds one slot at a time.
\item The log-FM cooperad $\cC^{\log\FM}$ requires the snc pair
$(X,D)$: classical FM spaces $\overline{\FM}_n(X)$ do not have the
log structure needed for the planted-forest boundary strata. Without
the logarithmic extension, the codimension-two cancellation mechanism
(Mechanism~3 of \S3.10) would fail.
\end{enumerate}
These constraints are not deficiencies but structural features: they
encode the geometry of the moduli space in the algebraic formalism.

\medskip
\noindent\textbf{Heisenberg: the strict chart suffices.}\enspace
For $\cH_k$, the convolution $sL_\infty$-algebra has $\ell_k=0$ for
$k\ge 3$ (the homotopy chiral algebra is strict, so all higher
cooperadic decompositions produce zero). The strict chart equals the
full $L_\infty$ structure: $\Convstr(\cC,\End(\cH_k))=\Convinf(\cC,\End(\cH_k))$.
Consequently, gauge equivalence in the strict chart is gauge
equivalence in the full $L_\infty$ structure, and the MC moduli
is computed by the strict dg Lie algebra alone. This is the
Gaussian simplification: the deformation theory of $\cH_k$ is
controlled by a classical (non-homotopical) Lie algebra.

\medskip
\noindent\textbf{Virasoro: the full $L_\infty$ is essential.}\enspace
For $\Vir_c$, the higher brackets $\ell_k$ for $k\ge 3$ are nonzero
(reflecting the infinite $A_\infty$-depth). The strict chart and the
$L_\infty$ structure have the same MC moduli (MC elements are the
same), but different notions of gauge equivalence: two MC elements
that are $L_\infty$-gauge-equivalent may not be strictly gauge-equivalent.
The full $L_\infty$ structure is needed for the formality theorem
(the shadow obstruction tower is a formality obstruction tower in the
$L_\infty$ sense) and for the transfer theorem (transferring the MC
element to cohomology requires the $\infty$-morphism data).

\subsection*{3.7.\enspace Assembly}

The modular convolution $L_\infty$-algebra:
\begin{equation}\label{eq:pref-convolution}
\mathfrak g^{\mathrm{mod}}_\cA:=\Convinf\!\Bigl(\cC^{\log\mathrm{FM}}_{\mathrm{mod}},\operatorname{End}_{\mathrm{Ch}_\infty}(A^{\mathrm{ch}}_\infty)\Bigr).
\end{equation}
The cooperadic input is the log-FM chain cooperad
$\cC^{\log\mathrm{FM}}_{\mathrm{mod}}$; the operadic input is the
$\mathrm{Ch}_\infty$-endomorphism operad of
$A^{\mathrm{ch}}_\infty$. The $E_1$ cousin
$\mathfrak g^{\mathrm{mod},E_1}_\cA$ uses the ribbon-graph-indexed
cooperad and the ordered bar endomorphism operad.

One-slot convention: fix the log-FM (resp.\ ribbon) cooperad as the
``geometric'' slot; vary the chiral algebra input as the ``algebraic''
slot by $\infty$-morphisms.

The \emph{strict chart}: the coderivation dg Lie algebra
\[
\mathfrak g^{\mathrm{mod},\log}_\cA(\mathfrak U):=\Convstr\!\bigl(\cC^{\log\mathrm{FM}}_{\mathrm{mod}},\operatorname{End}_{\mathrm{Ch}_\infty}(A^{\mathrm{ch}}_\infty)\bigr)
\]
has classical commutator bracket, no higher $L_\infty$ brackets, but
the same Maurer--Cartan moduli. The strict chart suffices for
constructing $\Theta_\cA$ and computing shadows; the full $L_\infty$
structure is needed for transfer, formality, and gauge equivalence.

\subsection*{3.8.\enspace The modular bar functor}

In log-FM coordinates,
\[
\mathrm B^{\log}_{\mathrm{mod}}(\cA)(g,n)=\bigoplus_{\Gamma\in\mathsf{Gr}^{\mathrm{st}}_{g,n}}\left(\bigotimes_{v\in V(\Gamma)}\bar B^{\mathrm{ch}}(A^{\mathrm{ch}}_\infty;\operatorname{In}(v))\otimes C_\bullet(\mathrm{FM}^{\log}_\Gamma)\otimes\orline{E_{\mathrm{int}}(\Gamma)}\right)_{\!\operatorname{Aut}(\Gamma)}.
\]
The ingredients: at each vertex the transferred
$\mathrm{Ch}_\infty$-bar contribution on its incoming half-edges;
at each internal edge the propagator $P_\cA=H_\cA^{-1}$; the geometric
factor $C_\bullet(\mathrm{FM}^{\log}_\Gamma)$; the orientation line
$\orline{E_{\mathrm{int}}(\Gamma)}=\det(\Bbbk E(\Gamma))\otimes\det(H_1(\Gamma;\Bbbk))^{-1}$;
the automorphism quotient.

\subsection*{3.9.\enspace The six-component differential}

The total differential has six components, whose mutual cancellations
constitute $D^2=0$:
\[
D^{\log}_{\mathrm{mod}}=\underbrace{d_{\check C}}_{\text{\v Cech}}+\underbrace{d_{\mathrm{Ch}_\infty}}_{\text{transferred chiral}}+\underbrace{d_{\mathrm{coll}}}_{\text{collision}}+\underbrace{d_{\mathrm{sew}}}_{\text{separating}}+\underbrace{d_{\mathrm{pf}}}_{\text{planted-forest}}+\underbrace{\hbar\Delta}_{\text{genus-raising}}.
\]
$d_{\check C}$ is the \v Cech differential of the cover, acting on
\v Cech indices. $d_{\mathrm{Ch}_\infty}$ is the transferred chiral
differential on each vertex, from secondary Borcherds operations.
$d_{\mathrm{coll}}$ contracts an internal edge by extracting the OPE
residue at the corresponding codimension-one collision stratum of
$\overline{\mathrm{FM}}_n(X)$. The three positive-genus boundary
operators act on a pure tensor $a\otimes\eta$ indexed by $\Gamma$:
\begin{align*}
d_{\mathrm{sew}}(a\otimes\eta)&=\sum_{e\in E_{\mathrm{sep}}(\Gamma)}\pm\mu_e(a)\otimes(\xi_e)_*\operatorname{Res}_{D_e^{\log}}(\eta),\\
d_{\mathrm{pf}}(a\otimes\eta)&=\sum_{F\in\mathsf{PF}^{\mathrm{rig}}(\Gamma)}\pm\mu_F(a)\otimes(\xi_F)_*\operatorname{Res}_{D_F^{\log}}(\eta),\\
\hbar\Delta(a\otimes\eta)&=\hbar\sum_{e\in E_{\mathrm{ns}}(\Gamma)}\pm\operatorname{Tr}_e(a)\otimes(\xi_e)_*\operatorname{Res}_{D_e^{\log}}(\eta).
\end{align*}
Separating edges give the clutching morphism (gluing two lower-genus
curves); non-separating edges give the genus-raising self-gluing
(BV operator); planted-forest strata give the genuinely logarithmic
corrections from Mok. Explicitly,
\[
d_{\mathrm{pf}}=\sum_{\rho\in\mathsf{PF}^{\mathrm{rig}}}\epsilon_\rho(\kappa_\rho)_*\mathrm{pr}_\rho^*\otimes\mu_\rho:
\]
Mok's degeneration formula internalised as a summand of the total
differential.

\subsection*{3.10.\enspace $D^2=0$}

The nilpotence $(D^{\log}_{\mathrm{mod}})^2=0$ holds by three
cancellation mechanisms. \emph{Vertex labels}: $d_{\check C}^{\,2}=0$,
$d_{\mathrm{Ch}_\infty}^{\,2}=0$, and
$\{d_{\check C},d_{\mathrm{Ch}_\infty}\}=0$ by the
$\mathrm{Ch}_\infty$-algebra axioms on $A^{\mathrm{ch}}_\infty$.
\emph{One-edge expansions}: anticommutators of a vertex differential
with an edge-contraction differential vanish by the Leibniz rule for
coderivations. \emph{Codimension-two cancellation}: the sum of all
products of two distinct edge-contraction operators vanishes, because
the codimension-two boundary of Mok's log-FM compactification is a
normal-crossings divisor (Mok, Theorem~3.3.1) and each codimension-two
face appears as the intersection of exactly two codimension-one faces
with opposite orientations.

The third mechanism is the nontrivial one. The normal-crossings
property is essential: without it, codimension-two faces could have
excess intersection, and the cancellation would fail.

\medskip
\noindent\textbf{The three mechanisms in detail.}\enspace
Expand $D^2$ into a $6\times 6$ matrix of anticommutators:
\[
D^2=\sum_{1\le i\le j\le 6}\{d_i,d_j\},
\]
where $d_1,\ldots,d_6$ are the six components of \S3.9.
\begin{enumerate}[label=\textup{Mechanism~\arabic*.},leftmargin=*]
\item \textbf{Vertex labels} ($i,j\in\{1,2\}$): six terms.
$d_{\check C}^2=0$ is the \v Cech identity.
$d_{\mathrm{Ch}_\infty}^2=0$ is the $A_\infty$-axiom.
$\{d_{\check C},d_{\mathrm{Ch}_\infty}\}=0$ is the compatibility
of the \v Cech differential with the transferred chiral structure.
These three vanish independently of the genus data.

\item \textbf{One-edge expansions} ($i\in\{1,2\}$, $j\in\{3,4,5,6\}$):
eight terms. Each computes $\{d_{\mathrm{vertex}},d_{\mathrm{edge}}\}$.
Because the edge-contraction operators act as coderivations on the
coalgebra underlying the bar complex, the Leibniz rule gives
$\{d_{\mathrm{vertex}},d_{\mathrm{edge}}\}(\gamma)=
d_{\mathrm{edge}}(d_{\mathrm{vertex}}\gamma)+
(-1)^{|d_{\mathrm{vertex}}|}d_{\mathrm{vertex}}(d_{\mathrm{edge}}\gamma)$,
and the two terms cancel by the vertex axioms applied to each half
of the coderivation split.

\item \textbf{Codimension-two cancellation} ($i,j\in\{3,4,5,6\}$):
ten terms. Each computes $\{d_{\mathrm{edge}_i},d_{\mathrm{edge}_j}\}$
where the two edge operators correspond to two distinct
codimension-one boundary strata. Their product is supported on the
codimension-two intersection. The normal-crossings property of
$\overline{\FM}_n^{\log}(X|D)$ ensures that this intersection is
transversal, and each codimension-two face is reached from exactly
two codimension-one faces with opposite orientation signs. The
cancellation in pairs is the higher-genus analogue of the genus-$0$
identity $\partial^2=0$ on the associahedron.
\end{enumerate}

\medskip
\noindent\textbf{$D^2=0$ at genus~$1$: explicit check.}\enspace
At $(g,n)=(1,1)$, the total differential has three terms:
$d_{\mathrm{Ch}_\infty}$ (from the vertex),
$d_{\mathrm{coll}}$ (from collision, a tree-level edge contraction
within the self-loop), and $\hbar\Delta$ (the genus-raising self-gluing).
The identity $D^2=0$ at $(1,1)$ reduces to
\[
d_{\mathrm{Ch}_\infty}^2+\{d_{\mathrm{Ch}_\infty},\hbar\Delta\}+(\hbar\Delta)^2=0.
\]
The first term vanishes by $A_\infty$. The cross-term
$\{d_{\mathrm{Ch}_\infty},\hbar\Delta\}=0$ by the one-edge expansion
mechanism. The last term $(\hbar\Delta)^2$ computes: the BV operator
applied twice contracts two pairs of legs, but at $(1,1)$ there is
only one self-loop, so $\Delta^2|_{(1,1)}=0$ by degree count (no
codimension-two stratum). Each mechanism kills its terms
independently; $D^2=0$ holds.

\medskip
\noindent\textbf{$D^2=0$ at genus~$2$: the nontrivial cancellation.}\enspace
At $(g,n)=(2,0)$, the codimension-two cancellation mechanism is first
exercised nontrivially. The three boundary divisors of
$\overline{\cM}_2$ (figure-eight, sunset, separating barbell from
\S3.2) meet pairwise in codimension-two strata.
The figure-eight and sunset share a codimension-two stratum
(contracting the figure-eight to a point that lies on one of the
three sunset edges). The two edge-contraction operators produce
opposite signs at this intersection because the normal-crossings
structure on $\overline{\cM}_2$ gives opposite orientations to the
two orderings of the contracted edges. This is the first instance
where the third cancellation mechanism is genuinely needed, and
where the normal-crossings property of the Mok compactification (not
just the Deligne--Mumford compactification) plays a role.

\subsection*{3.11.\enspace The $E_n$ hierarchy in modular homotopy theory}

The modular homotopy theory of \S\S3.1--3.10 has been presented in the
$E_\infty$ (symmetric) setting. The $E_1$ (ordered) setting is more
fundamental: every construction above has a primitive $E_1$ version
from which the $E_\infty$ version is derived by averaging.

\medskip
\noindent\textbf{$E_1$-modular operads: ribbon graphs.}\enspace
The $E_1$-modular operad uses the Feynman transform of $\Ass$
(instead of $\Com$): operations indexed by ribbon graphs (fatgraphs)
with cyclic ordering at each vertex. The $E_1$ convolution algebra
\[
\mathfrak g^{\mathrm{mod},E_1}_\cA:=\Convinf\bigl(F\!\Ass,\End_{\barB^{E_1}(\cA)}\bigr)
\]
carries the $R$-matrix data: the genus-$0$ binary shadow
$r(z)=\Res^{\mathrm{coll}}_{0,2}(\Theta^{E_1}_\cA)$ is a matrix-valued
function of the spectral parameter $z$, encoding the ordering of
OPE insertions. The coinvariant map
$\mathrm{av}\colon F\!\Ass\to F\Com$ projects
$\Theta^{E_1}_\cA\mapsto\Theta_\cA$: colour-ordered amplitudes to
full amplitudes, destroying the $R$-matrix.

\medskip
\noindent\textbf{$E_2$-chiral: the intermediate level.}\enspace
The chiral Hochschild complex $\ChirHoch^*(\cA,\cA)$ of an
$E_\infty$-chiral algebra $\cA$ carries an $E_2$-algebra structure
(chiral Gerstenhaber bracket from OPE residues on $\overline{\FM}_k(\bC)$).
This $E_2$ is the boundary algebra of the Swiss-cheese structure; the
pair $(\ChirHoch^*(\cA,\cA),\cA)$ is the $\SCchtop$-datum. The
$E_2$-chiral structure on Hochschild is the intermediate level between
$E_1$ (ordered bar) and $E_3$ (topologized derived centre).

\medskip
\noindent\textbf{$E_3$-topological: the topologized output.}\enspace
When $\cA$ has a conformal vector at non-critical level (Sugawara
$T(z)=\{Q,G(z)\}$), the chiral direction becomes $Q$-exact in
cohomology: the complex structure on $\bC$ becomes irrelevant, and
$\SCchtop$ collapses to $E_3$-topological. This is proved for
affine Kac--Moody $\widehat\fg_k$ at $k\neq -h^\vee$ (where
Sugawara is explicit); conjectural for general chiral algebras with
conformal vector. The proof is cohomological: it works on
$Q$-cohomology, not on cochains. For class-M algebras where
chain-level data is essential, the $E_3$-topological structure may
exist only on cohomology.

The $E_n$ hierarchy in modular homotopy theory is thus:
$E_1$~(ordered bar, $R$-matrix, Yangian)~$\to$~$E_2$~(chiral Hochschild, Gerstenhaber)~$\to$~$E_3$~(topologized derived centre,
requires conformal vector). Each step is a genuine loss of
structure (the averaging map $E_1\to E_\infty$ loses the
$R$-matrix; the topologization $\SCchtop\to E_3$ loses the chiral
direction). The ordered bar $\barB^{\mathrm{ord}}(\cA)$ sits at the
$E_1$ level and is the primary object of the theory.


% ====================================================================
\section*{4.\quad The universal Maurer--Cartan element}
% ====================================================================

The modular convolution algebra $\gAmod$ is a complete filtered
$L_\infty$-algebra (\S3.7). Its total differential
$D_\cA$ already squares to zero. Decomposing $D_\cA=d_0+\Theta_\cA$
into a tree-level local part and its complement produces a universal
element $\Theta_\cA\in\operatorname{MC}(\gAmod)$ satisfying the
Maurer--Cartan equation as a formal consequence of $D_\cA^2=0$. This
element requires no equation to solve and no convergence hypothesis.
Every invariant in this survey is a projection of~$\Theta_\cA$: the
five theorems A--D and H are its five $\Sigma_n$-coinvariant shadows.

\subsection*{4.1.\enspace $\Gamma$-amplitudes and Taylor coefficients}

Each stable graph produces a multilinear operation on the convolution
algebra, built from chiral operations at vertices, propagators along
edges, and geometric factors from log-FM strata. For
$\Gamma\in\mathsf{Gr}^{\mathrm{st}}$ with $|V(\Gamma)|=k$ vertices and
elements $f_1,\ldots,f_k\in\gAmod$, the \emph{$\Gamma$-amplitude}
assembles
\[
\ell_\Gamma(f_1,\ldots,f_k)=\mu_\Gamma\circ(\alpha^{\mathrm{mod}}_\Gamma\otimes f_1\otimes\cdots\otimes f_k)\circ\Delta^{\log}_\Gamma,
\]
a $k$-linear map of cohomological degree $2-2g(\Gamma)-k$. Here
$\mu_\Gamma$ is the graph composition (transferred chiral operations
at vertices, propagators along edges), $\alpha^{\mathrm{mod}}_\Gamma$
is the modular twisting morphism component, and $\Delta^{\log}_\Gamma$
is the cooperadic cocomposition.

The Taylor coefficients of the modular $L_\infty$ structure sum over
stable graphs of fixed genus and vertex count:
\[
\ell_k^{(g)}=\sum_{\substack{\Gamma\in\mathsf{Gr}^{\mathrm{st}},\;|V(\Gamma)|=k\\b_1(\Gamma)+\sum_v g(v)=g}}\frac{1}{|\operatorname{Aut}(\Gamma)|}\ell_\Gamma.
\]
The homotopy Jacobi identity is encoded by $D^2=0$ on the total
convolution algebra.

\medskip
\noindent\textbf{Low-order Taylor coefficients.}\enspace
At tree level, the binary bracket is the transferred Lie bracket:
$\ell_2^{(0)}(\alpha,\beta)=\pi[m_2(\iota(\alpha),\iota(\beta))]$.
The ternary bracket sums over the three binary trees in
$\mathsf{Trees}_3$ (channels $s$, $t$, $u$), each inserting a homotopy
$h$ at the internal edge. The quaternary bracket sums over the
fifteen labeled trees in $\mathsf{Trees}_4$ (two unlabeled topologies:
three balanced $((ab)(cd))$ and twelve caterpillar $(((ab)c)d)$),
each with two propagator insertions; this is the classical homological
perturbation lemma in its $L_\infty$ incarnation.

The first genus-raised bracket is unary, the BV operator on the single
graph with one vertex and one self-loop:
\[
\ell_1^{(1)}(\alpha)=\operatorname{tr}(P_\cA\circ\alpha\circ\delta^{\mathrm{ns}})=\sum_i\langle e^i,\alpha(e_i)\rangle_{\mathrm{Sh}},
\]
trace over the propagator contracting two half-edges at the
non-separating node of $\overline{\cM}_{1,1}$. The genus-one binary
bracket
\[
\ell_2^{(1)}(\alpha,\beta)=\operatorname{tr}\bigl(P_\cA\circ m_2(\iota\alpha,-)\circ\delta^{\mathrm{ns}}\circ\iota\beta\bigr)+(\alpha\leftrightarrow\beta)
\]
accounts for the separating node of $\overline{\cM}_{1,2}$. These
low-order brackets are the only data needed for shadow computations
through degree~$4$.

\subsection*{4.2.\enspace The bar-intrinsic construction}

$\Theta_\cA$ requires no equation to solve: it is extracted from a
differential that already squares to zero.

Decompose the total bar differential
$D_\cA\colon\mathrm B^{\mathrm{mod}}(\cA)\to\mathrm B^{\mathrm{mod}}(\cA)$
as $D_\cA=d_0+\Theta_\cA$, where
$d_0=d_{\mathrm{int}}+[\tau,-]$ is the tree-level local part. The
\emph{universal Maurer--Cartan element} is the remainder,
\begin{equation}\label{eq:pref-theta}
\Theta_\cA:=D_\cA-d_0=\sum_{\Gamma\in\mathsf{Gr}^{\mathrm{st}}}\frac{W^{\log\mathrm{FM}}_\Gamma}{|\operatorname{Aut}(\Gamma)|}\otimes\Phi^\cA_\Gamma\in\operatorname{MC}(\gAmod),
\end{equation}
with $W^{\log\mathrm{FM}}_\Gamma\in H^*(\overline{\cM}^{\log}_{g(\Gamma),n(\Gamma)})$
the log-FM fundamental class of the stratum and
$\Phi^\cA_\Gamma\in\Hom(\bar\cA^{\otimes n(\Gamma)},\Bbbk)$ the chiral
amplitude (propagators on internal edges, operations at vertices,
cyclic trace at the output).

The MC property is immediate. $D_\cA^2=0$ by the normal-crossings
property of $\overline{\cM}_{g,n}^{\log}$; $d_0^2=0$ by construction;
expanding $(d_0+\Theta_\cA)^2=0$ gives
\[
[d_0,\Theta_\cA]+\tfrac12[\Theta_\cA,\Theta_\cA]=0.
\]
The MC property is a formal consequence of $\partial^2=0$ on the
moduli space of curves, requiring no simple-Lie restriction, no
convergence hypothesis, and no choice of basis. This is MC2
(conjecture-turned-theorem) in its cleanest form.

\medskip
\noindent\textbf{Proof sketch.}\enspace
Write $D_\cA=d_0+\Theta_\cA$. Then
$0=D_\cA^2=d_0^2+d_0\Theta_\cA+\Theta_\cA d_0+\Theta_\cA^2
=d_0^2+[d_0,\Theta_\cA]+\Theta_\cA^2$.
Now $d_0^2=0$ and $\Theta_\cA^2=\tfrac12[\Theta_\cA,\Theta_\cA]$
(since $\Theta_\cA$ has odd cohomological degree); so
$[d_0,\Theta_\cA]+\tfrac12[\Theta_\cA,\Theta_\cA]=0$.
This is the MC equation. The proof requires:
(a)~$D_\cA^2=0$, which is \S3.10;
(b)~$d_0^2=0$, which is the genus-$0$ bar differential;
(c)~the decomposition $D_\cA=d_0+\Theta_\cA$, which is the definition
of $\Theta_\cA$ as the non-tree-level part. No further input is needed.

The $E_1$ analogue $\Theta^{E_1}_\cA$ is constructed identically on
the ordered, ribbon-graph-indexed convolution algebra, and
$\Theta_\cA=\mathrm{av}(\Theta^{E_1}_\cA)$ under the coinvariant map
$F\!\Ass\to F\Com$.

\medskip
\noindent\textbf{Heisenberg: $\Theta_{\cH_k}$ collapses to a
scalar.}\enspace For the Heisenberg algebra $\cH_k$, the only
nonvanishing graph amplitude is on the single-edge graph
$\Gamma_2$ (two vertices, one edge): $\Phi^{\cH_k}_{\Gamma_2} = k$
(the level). Every graph with $|E| \ge 2$ vanishes because the only
OPE mode is $\alpha_{(1)}\alpha = k$, and two propagator insertions
on the same vertex yield zero by degree. Hence
$\Theta_{\cH_k} = k \cdot \eta_{\mathrm{univ}} \otimes
\Lambda_{\mathrm{univ}}$: the MC element is a scalar multiple of
the universal class. The genus-$g$ projection is
$F_g(\cH_k) = k \cdot \lambda_g^{\mathrm{FP}}$
\textup{(\textsc{uniform-weight})}. The modular characteristic
$\kappa(\cH_k) = k$ is the sole surviving datum.

\medskip
\noindent\textbf{Kac--Moody: $\Theta_{\widehat\fg_k}$ terminates at
degree~$3$.}\enspace
For the affine Kac--Moody algebra $\widehat\fg_k$, the graph
amplitudes at degree $r\le 3$ are:
\begin{itemize}
\item Degree~$2$: the single-edge graph gives
$\Phi_{\Gamma_2}=k\,\Omega=k\sum_a t^a\otimes t^a$ (the Casimir, with
level prefix; at $k=0$, $\Phi=0$). Averaging:
$\mathrm{av}(\Phi_{\Gamma_2})=\kappa=(k+h^\vee)\dim\fg/(2h^\vee)$.
\item Degree~$3$: the trivalent tree gives
$\Phi_{\Gamma_3}(a,b,c)=\kappa([a,b],c)$, where $[\cdot,\cdot]$ is
the Lie bracket and $(\cdot,\cdot)$ the Killing form. This is the
cubic shadow $S_3=\mathfrak C$.
\item Degree~$4$: the quartic amplitude vanishes on bar cohomology
by the Jacobi identity. The transferred quartic bracket
$\ell_4^{(0)}$ on $H^*(\barB(\widehat\fg_k))$ is zero because
Jacobi forces the quartic obstruction class to be exact.
\end{itemize}
$\Theta_{\widehat\fg_k}$ is determined by $(\kappa,\mathfrak C)$
with $S_r=0$ for $r\ge 4$: class~L, $r_{\max}=3$.

\medskip
\noindent\textbf{Virasoro: $\Theta_{\Vir_c}$ is infinite.}\enspace
For Virasoro at central charge~$c$:
\begin{itemize}
\item Degree~$2$: $\kappa=c/2$.
\item Degree~$3$: the cubic shadow is nonzero; $S_3$ arises from
the simple-pole OPE $T(z)T(w)\sim 2T(w)/(z-w)^2+\cdots$, which
produces a Lie-bracket-like structure on the one-dimensional bar
cohomology spanned by the class dual to~$T$.
\item Degree~$4$: $S_4=10/[c(5c+22)]$ (the quartic contact invariant).
Nonzero for all $c\neq 0,-22/5$. No Jacobi identity kills it.
\item Degree~$r\ge 5$: the Poisson bracket $\{S_3,S_4\}_H$ generates
$S_5$, and induction produces nonvanishing $S_r$ at all orders.
\end{itemize}
$\Theta_{\Vir_c}$ is an infinite MC element: class~M,
$r_{\max}=\infty$. The entire infinite tower is algebraic of
degree~$2$, governed by~\eqref{eq:preface-riccati-hook}.

\subsection*{4.3.\enspace $\Theta_\cA$ as universal modular twisting morphism}

The Maurer--Cartan space of the modular convolution $L_\infty$
algebra is identified with the space of modular twisting morphisms,
\[
\operatorname{MC}_\bullet(\gAmod)\simeq\operatorname{Tw}_{\alpha^{\mathrm{mod}}}\Bigl(\cC^{\log\mathrm{FM}}_{\mathrm{mod}},\operatorname{End}_{\mathrm{Ch}_\infty}(A^{\mathrm{ch}}_\infty)\Bigr).
\]
Under this identification $\Theta_\cA$ is the \emph{universal modular
twisting morphism}, the operadic analogue of the canonical flat
connection on a principal bundle. A twisting morphism
$\alpha\colon\cC\to\cP$ determines a twisted composition product
$\cC\circ_\alpha\cP$ whose differential squares to zero iff $\alpha$
satisfies the MC equation. $\Theta_\cA$ is the unique twisting
morphism that simultaneously twists the modular bar complex and
intertwines with the log-FM boundary structure.

The principal-bundle analogy is exact. The modular bar bundle
$\mathrm B^{\log}_{\mathrm{mod}}(\cA)\to\overline{\cM}_{g,n}$ is the
principal bundle; $\Theta_\cA$ is the connection; the MC equation is
flatness; the shadow tower (\S6) is the Chern--Weil theory. The
structure group is the pro-unipotent MC gauge group
$\exp(\mathfrak g^{\mathrm{mod},0}_\cA)$.

\medskip
\noindent\textbf{The twisting morphism in low degrees.}\enspace
At genus~$0$, degree~$2$: the twisting morphism component
$\alpha^{\mathrm{mod}}_{0,2}\colon\cC^{\log\FM}(0,2)\to\End(A)$ is the
chiral product $\mu_\cA$. The twisted composition gives the
bar differential $d_B=\sum_k m_k$ (sum of all $A_\infty$-operations).
At genus~$0$, degree~$3$: the component
$\alpha^{\mathrm{mod}}_{0,3}\colon\cC^{\log\FM}(0,3)\to\End(A)$ uses
the chain map $C_*(\overline{\cM}_{0,4})\to\End(A)$ from the three
boundary points of $\overline{\cM}_{0,4}\cong\bP^1$ to the three OPE
channels. At genus~$1$, degree~$1$: the component
$\alpha^{\mathrm{mod}}_{1,1}\colon\cC^{\log\FM}(1,1)\to\End(A)$ is the
BV operator $\hbar\Delta$, using the chain of the boundary divisor
$\delta_{\mathrm{irr}}\in\overline{\cM}_{1,1}$.

\medskip
\noindent\textbf{Uniqueness of the twisting morphism.}\enspace
On the Koszul locus, $\Theta_\cA$ is unique up to MC gauge
equivalence. The tree-level complex carries a contracting homotopy
(from PBW degeneration), so the obstruction to existence at each
genus is exact, and the solution is determined up to gauge by
induction from genus~$0$. Different choices of contracting homotopy
yield gauge-equivalent MC elements; no free parameters appear at
any genus. Off the Koszul locus: the twisting morphism still exists
(bar-intrinsic), but uniqueness up to gauge may fail (the
contracting homotopy may not exist, and the obstruction classes may
have nontrivial cohomology).

\subsection*{4.4.\enspace Tridegree, depth, and convergence}

Each coefficient of $\Theta_\cA$ carries a natural tridegree
\[
(g,n,d)=(\text{loop genus},\text{external degree},\text{log boundary depth}),
\]
with $d(\rho)=\#E_{\mathrm{sep}}(\Gamma_\rho)+\#E_{\mathrm{ns}}(\Gamma_\rho)+\operatorname{depth}_{\mathrm{pf}}(\Gamma_\rho)$
the codimension of the log-FM stratum. The depth filtration
$F^d\gAmod=\bigoplus_{d'\ge d}(\gAmod)_{*,*,d'}$ makes the convolution
algebra complete:
\[
\gAmod=\varprojlim_d\gAmod/F^d\gAmod.
\]
The inverse limit $\Theta_\cA=\varprojlim_r\Theta_\cA^{\le r}$
converges unconditionally: no analytic input, no growth estimate, no
restriction on the algebra. Convergence is purely algebraic,
guaranteed by completeness of the depth filtration. This is MC4
(completion tower): proved. Generating depth (the degree at
which higher operations are determined by lower ones) is distinct
from algebraic depth (whether the tower terminates).

At fixed $(g,n)$, only finitely many stable graph types contribute.
The depth filtration refines this further: at depth $d$, the stratum
has codimension $d$ in $\overline{\cM}_{g,n}^{\log}$, and the
amplitude has internal-edge count bounded by $d$.

\medskip
\noindent\textbf{Generating depth versus algebraic depth.}\enspace
Two distinct notions of depth govern $\Theta_\cA$:
\begin{itemize}
\item \emph{Generating depth} $d_{\mathrm{gen}}(\cA)$: the smallest
$r$ such that all $m_s$ for $s>r$ in the minimal $A_\infty$-model
are determined (as algebraic consequences) by $m_2,\ldots,m_r$.
For Virasoro: $d_{\mathrm{gen}}=3$ (the ternary operation $m_3$
generates all higher $m_s$ recursively).
\item \emph{Algebraic depth} $d_{\mathrm{alg}}(\cA)$: the smallest
$r$ such that $m_s=0$ for all $s>r$ in the minimal model, or
$\infty$ if no such $r$ exists. For Virasoro:
$d_{\mathrm{alg}}=\infty$ (all $m_s$ are nonzero, class~M).
\end{itemize}
The two are independent: $d_{\mathrm{gen}}=3$ and
$d_{\mathrm{alg}}=\infty$ coexist for Virasoro. The shadow depth
$r_{\max}$ equals $d_{\mathrm{alg}}$: it records whether the tower
terminates, not whether the tower is finitely generated.

\medskip
\noindent\textbf{Convergence is unconditional.}\enspace
The inverse limit $\Theta_\cA=\varprojlim_r\Theta_\cA^{\le r}$ exists
for \emph{every} chiral algebra $\cA$, without any analytic hypothesis.
The argument:
\begin{enumerate}[label=(\roman*)]
\item The convolution algebra $\gAmod$ is complete with respect to the
depth filtration $F^d$: $\gAmod=\varprojlim_d\,\gAmod/F^d$.
\item At each depth $d$, the truncation
$\Theta_\cA^{\le d}\in\gAmod/F^{d+1}$ is a finite sum over stable
graphs with at most $d$ internal edges.
\item The transition maps $\gAmod/F^{d+1}\to\gAmod/F^d$ are
surjective (by the bar-intrinsic construction, which solves all
obstruction classes simultaneously).
\item The Mittag-Leffler condition holds: the inverse system has
surjective transitions, so $\varprojlim^1=0$, and the inverse limit
is exact.
\end{enumerate}
No growth estimate, no radius of convergence, no restriction on
$\kappa$ or the depth class is needed. The convergence is algebraic,
not analytic: it is a consequence of the completeness of a
pro-nilpotent filtration on a graded vector space, with no metric
structure required.

\subsection*{4.5.\enspace The weight filtration}

Decompose the MC equation by internal-edge count,
\[
\Theta_\cA=\sum_{r\ge 1}\Theta^{[r]}_\cA,\qquad\Theta^{[r]}_\cA=\sum_{\substack{\Gamma\in\mathsf{Gr}^{\mathrm{st}}\\|E_{\mathrm{int}}(\Gamma)|=r}}\frac{W^{\log\mathrm{FM}}_\Gamma}{|\operatorname{Aut}(\Gamma)|}\otimes\Phi^\cA_\Gamma.
\]
Weight~$1$: $[D_{\mathrm{loc}},\Theta^{[1]}_\cA]=0$. Weight~$N$:
$[D_{\mathrm{loc}},\Theta^{[N]}_\cA]+\tfrac12\sum_{i+j=N}[\Theta^{[i]}_\cA,\Theta^{[j]}_\cA]=0$.
The obstruction to extending from weight $N-1$ to weight $N$ lies in
$H^2(\gAmod/F^{N+1},D_{\mathrm{loc}})$. The bar-intrinsic
construction solves all stages simultaneously.

\medskip
\noindent\textbf{Weight~$1$: boundary divisors.}\enspace
In degree $(0,4)$: the three boundary points of
$\overline{\cM}_{0,4}\cong\mathbb P^1$ correspond to the three
channels $(12|34)$, $(13|24)$, $(14|23)$,
\[
\Theta^{[1]}_\cA\big|_{(0,4)}=[\delta_s]\otimes\Phi_s+[\delta_t]\otimes\Phi_t+[\delta_u]\otimes\Phi_u.
\]
The weight-one equation $\Phi_s+\Phi_t+\Phi_u=F_3$ identifies the
Jacobiator homotopy with a boundary in the bar complex: the first
Borcherds identity. In degree $(1,1)$: the single boundary divisor
$\delta_{\mathrm{irr}}$ gives
$\Theta^{[1]}_\cA|_{(1,1)}=[\delta_{\mathrm{irr}}]\otimes\Delta$ with
$\Delta=\sum_i e_i\otimes e^i$ the Casimir.

In degree $(0,5)$: the ten boundary divisors of $\overline{\cM}_{0,5}$
form the Petersen graph (each divisor is a product of two
$\overline{\cM}_{0,4}$'s meeting at a node). The weight-one equation
at $(0,5)$ produces the \emph{pentagon identity}: the five ways to
parenthesise $(((ab)c)d)e,\ldots,a(b(c(de)))$ are related by a
cycle of four associator homotopies, closing by the fifth. In the
$A_\infty$ framework, this is the $m_4$-equation:
\[
\partial m_4+m_2(m_3\otimes\id+\id\otimes m_3)+m_3(m_2\otimes\id\otimes\id+\cdots)=0.
\]
The pentagon identity is the degree-$(0,5)$ component of the MC
equation; the entire $A_\infty$ hierarchy is the tree-level
projection of a single MC element.

\medskip
\noindent\textbf{Heisenberg: all weights collapse.}\enspace
For $\cH_k$, the weight-one component $\Theta^{[1]}_{\cH_k}$ at
$(0,4)$ has $\Phi_s=\Phi_t=\Phi_u=0$ (no cubic OPE pole, so no
Jacobiator), and $\Theta^{[1]}|_{(1,1)}=k\cdot[\delta_{\mathrm{irr}}]$
(the curvature $\kappa=k$). All higher weight components
$\Theta^{[r]}_{\cH_k}=0$ for $r\ge 2$. The MC element is entirely
determined by the weight-one data, which is a single scalar.

\medskip
\noindent\textbf{Kac--Moody: weight~$1$ carries the Lie bracket.}\enspace
For $\widehat\fg_k$, the weight-one component at $(0,4)$ has
$\Phi_s(a,b,c,d)=\kappa([a,b],[c,d])$ (the structure constants
of $\fg$ contracted through the Killing form). The
weight-one equation at $(0,4)$ is the Jacobi identity. At
$(1,1)$: $\Theta^{[1]}|_{(1,1)}=\kappa\cdot[\delta_{\mathrm{irr}}]$.
Weight~$2$: the planted-forest correction enters through the
log-FM degeneration, but it is killed by the Jacobi identity at
degree~$4$. For $\widehat\fg_k$, weights~$\ge 2$ contribute only
through the genus-raising BV operator; no planted-forest or
degree-raising corrections survive.

\medskip
\noindent\textbf{Weight~$2$: the first planted-forest layer.}\enspace
At weight~$2$, codimension-two strata enter: classical products of
two boundary divisors plus genuinely logarithmic planted-forest
strata with no DM counterpart. The weight-two equation is
$[D_{\mathrm{loc}},\Theta^{[2]}_\cA]=-\tfrac12[\Theta^{[1]},\Theta^{[1]}]$,
and the planted-forest correction $\Theta^{[2]}_{\mathrm{pf}}$ records
how collision limits in $\mathrm{FM}_n(X|D)$ correct the naive square.
For the $\mathcal W_3$ central-parameter line, cubic gauge triviality
kills the weight-$2$ obstruction; the first genuine invariant appears
at weight~$3$.

\subsection*{4.6.\enspace The all-genus recursion}

Projecting the MC equation to fixed $(g,n)$,
\[
d\Theta^{(g,n)}_\cA+\tfrac12\!\!\!\sum_{\substack{g_1+g_2=g\\n_1+n_2=n+2}}\!\!\!\ell_2^{(0)}(\Theta^{(g_1,n_1)}_\cA,\Theta^{(g_2,n_2)}_\cA)+\Delta_{\mathrm{ns}}\Theta^{(g-1,n+2)}_\cA+\sum_{k\ge 3}\frac{1}{k!}\ell_k^{(\mathrm{tree})}(\Theta_\cA,\ldots,\Theta_\cA)^{(g,n)}=0.
\]
Four terms: the internal differential, separating clutching,
non-separating BV, and planted-forest corrections. This recursion
determines $\Theta^{(g,n)}_\cA$ inductively from lower $(g',n')$ in
lexicographic order. The base cases are
$\Theta^{(0,3)}_\cA$ (the chiral bracket) and $\Theta^{(0,4)}_\cA$
(the Jacobiator data). The recursion terminates at each $(g,n)$.

\medskip
\noindent\textbf{The clutching identity.}\enspace
On each rigid boundary stratum~$\rho$,
\[
\Theta_\cA\big|_\rho=(\kappa_\rho)_*\!\left(\bigotimes_{v\in V(S_\rho)}\Theta_{\cA,v}\right).
\]
The amplitude on the degenerate curve equals the product of amplitudes
on the irreducible components, sewn by propagators along the nodes.
This is the MC-level sewing axiom, and the starting point for the
clutching law of the quartic shadow (\S6).

\medskip
\noindent\textbf{Recursion at genus~$1$.}\enspace
At $(g,n)=(1,0)$ (genus~$1$, no marked points), the recursion
simplifies to
\[
d\Theta^{(1,0)}_\cA+\Delta_{\mathrm{ns}}\Theta^{(0,2)}_\cA=0.
\]
The separating clutching term vanishes (no way to split
$(g_1,n_1)\sqcup(g_2,n_2)$ with $g_1+g_2=1$ and $n_1+n_2=2$ using
only tree-level data; the base case $(0,2)$ contributes through the
BV operator). The non-separating term computes
$\Delta_{\mathrm{ns}}\Theta^{(0,2)}_\cA=\sum_i\langle e^i,\Theta^{(0,2)}_\cA(e_i)\rangle$:
the contraction of the genus-$0$ binary amplitude (the chiral product)
by the propagator. The result is $\Theta^{(1,0)}=\kappa\cdot\lambda_1$
\textsc{(uniform-weight)}, the genus-$1$ amplitude. The computation
reduces to computing $\mathrm{tr}(P_\cA\circ m_2)=\kappa$, which is
the definition of the modular characteristic.

For Heisenberg: $\Theta^{(0,2)}_{\cH_k}=k$ (the level),
$P_{\cH_k}=1/k$, so $\Delta_{\mathrm{ns}}\Theta^{(0,2)}=k\cdot(1/k)=1$.
Hence $\Theta^{(1,0)}_{\cH_k}=\lambda_1$, and
$F_1(\cH_k)=\kappa/24=k/24$. The single stable graph at $(1,0)$
(the self-loop graph $\Gamma_{\mathrm{irr}}$) contributes
$(\hbar/2)\cdot\mathrm{tr}(P\circ m_2)=\kappa\hbar/2$.

\medskip
\noindent\textbf{Recursion at genus~$2$.}\enspace
At $(g,n)=(2,0)$, the recursion has three terms:
\begin{align*}
d\Theta^{(2,0)}_\cA&+\tfrac12\ell_2^{(0)}(\Theta^{(1,0)}_\cA,\Theta^{(1,0)}_\cA)\\
&+\Delta_{\mathrm{ns}}\Theta^{(1,2)}_\cA+\text{(planted-forest)}=0.
\end{align*}
The separating clutching $\tfrac12\ell_2^{(0)}(\Theta^{(1,0)},\Theta^{(1,0)})$
produces the separating barbell graph contribution: two genus-$1$
vertices connected by one edge. The non-separating BV
$\Delta_{\mathrm{ns}}\Theta^{(1,2)}$ produces the iterated BV and
the clutching-times-BV terms. These correspond to the three stable
graph types of $\overline{\cM}_2$ enumerated in \S3.2. The
planted-forest correction is genuinely logarithmic.

For Heisenberg at genus~$2$: only the iterated BV contributes
(the separating term involves $\ell_2^{(0)}(\Theta^{(1,0)},\Theta^{(1,0)})$,
which vanishes because the Heisenberg convolution bracket is abelian).
The result is $F_2(\cH_k)=7k/5760$.

For affine KM at genus~$2$: the separating term is nonzero (the
Lie bracket gives a nontrivial $\ell_2^{(0)}$), and the planted-forest
correction enters through the log-FM degeneration formula. The
Jacobi identity ensures that all terms combine to give
$F_2(\widehat\fg_k)=7\kappa(\widehat\fg_k)/5760$ \textsc{(uniform-weight)}.

\medskip
\noindent\textbf{Recursion at genus~$3$: five graph types.}\enspace
At $(g,n)=(3,0)$, the recursion involves five stable graph types:
(a)~the iterated figure-eight with three self-loops;
(b)~the barbell with one genus-$1$ and one genus-$2$ vertex;
(c)~the theta graph (three parallel edges between two genus-$0$ vertices,
with one self-loop at one vertex);
(d)~the triple-banana (three edges, each with one self-loop);
(e)~the complete graph $K_4$ on four genus-$0$ vertices.
For Heisenberg, only type~(a) contributes (all other types involve
Lie brackets or cubic shadows that vanish). The result:
$F_3(\cH_k)=31k/967680$ from the $\hat A$-genus.

For Virasoro at genus~$3$: all five types contribute, with the
planted-forest corrections carrying the quartic and quintic shadow
data. The genus-$3$ free energy
$F_3(\Vir_c)=31c/(2\cdot 967680)=31c/1935360$ \textsc{(uniform-weight)}.

\medskip
\noindent\textbf{The recursion as a Feynman diagram expansion.}\enspace
The recursion at $(g,n)$ is a sum over Feynman diagrams with $g$ loops
and $n$ external legs, weighted by the chiral amplitudes at each vertex
and the propagator $P_\cA=H_\cA^{-1}$ at each internal edge. The
structure is identical to the perturbative expansion of a quantum field
theory on the moduli space $\overline{\cM}_{g,n}$, with the bar complex
as the kinetic term and the shadow tower as the interaction vertices.
The 't~Hooft large-$N$ expansion corresponds to the genus filtration:
the colour-ordered amplitudes at genus~$g$ are weighted by
$\hbar^g=N^{-2g}$, and the planar ($g=0$) diagrams dominate.

The recursion terminates at each $(g,n)$ because the set of stable
graph types $\mathsf{Gr}^{\mathrm{st}}_{g,n}$ is finite. No
convergence hypothesis is needed: the recursion is finite at each step,
and the inverse limit over all $(g,n)$ converges by completeness of
the depth filtration (MC4).

\bigskip
\noindent
Every invariant in this monograph is a projection of $\Theta_\cA$:
the curvature $\kappa$, the spectral discriminant $\Delta_\cA$, the
shadow metric $Q_L$, the sewing amplitudes, the $\hat A$-genus, the
Fredholm determinant, and the quartic contact invariant
$Q^{\mathrm{contact}}$. The five main theorems are five projections.

\medskip
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lll}
\textbf{Projection of $\Theta_\cA$} & \textbf{Invariant} & \textbf{Section}\\
\hline
Scalar ($r=2$, genus tower) & $\kappa(\cA)$, $F_g$, $\hat A$-genus & \S2\\[1pt]
Binary genus-$0$ residue & classical $r$-matrix, Yangian seed & \S7.7\\[1pt]
Binary Verdier dual & complementarity $Q_g\oplus Q_g^!$ & \S2\\[1pt]
Bar-cobar counit & inversion $\Omega(\barB(\cA))\xrightarrow{\sim}\cA$ & \S1\\[1pt]
Chiral Hochschild & $\operatorname{ChirHoch}^*(\cA)$, deformation ring & \S9\\[1pt]
Spectral discriminant & $\Delta_\cA(x)$, genus-$1$ Hessian & \S5\\[1pt]
Cubic shadow ($r=3$) & gauge-trivial obstruction & \S6\\[1pt]
Quartic resonance ($r=4$) & $\mathfrak Q^{\mathrm{contact}}$, clutching law & \S6\\[1pt]
MC tautological descent & shadow CohFT, $R^*(\overline{\cM}_{g,n})$ & \S5\\[1pt]
Primitive kernel & shell equations, branch BV & \S5\\[1pt]
Dirichlet--sewing lift & $S_\cA(u)$, Euler--Koszul class & \S8\\[1pt]
Swiss-cheese colour decomposition & $\alpha_T$, six projections (Vol.~II) & \S10
\end{tabular}
\end{center}
\medskip

\noindent
These five theorems are five projections of $\Theta_\cA$. Theorem~A
constructs the arena in which $\Theta_\cA$ lives. Theorem~B
recovers $\cA$ from $\Theta_\cA$ on the Koszul locus. Theorem~C
splits the genus tower into Lagrangian summands (C1 unconditional, C2
\textsc{(uniform-weight)}). Theorem~D extracts the scalar $\kappa$
with $\hat A$-genus generating function (uniform-weight; multi-weight
adds $\delta F_g^{\mathrm{cross}}$). Theorem~H identifies the
deformation ring via $\operatorname{ChirHoch}^*$ concentration.

The finite-order projections form an obstruction tower
$\Theta_\cA^{\le 2}\to\Theta_\cA^{\le 3}\to\Theta_\cA^{\le 4}\to\cdots$
whose generating function is algebraic of degree~$2$. On each
primary line,
$H(t)=t^2\sqrt{Q_L(t)}$ is determined by three seed invariants
$(\kappa,\alpha,S_4)$. The inverse limit exists and is automatically
Maurer--Cartan because $D_\cA^2=0$ (MC4).

In three dimensions, $\Theta_\cA$ extends to an open/closed
Maurer--Cartan element
$\Theta^{\mathrm{oc}}_\cA=\Theta_\cA+\sum_j\mu^{M_j}$
packaging the holomorphic-topological QFT on
$\mathbb C_z\times\mathbb R_t$: the bar complex $B(\cA)$, coassociative over $(\mathrm{ChirAss})^!$,
supplies the holomorphic factorization data; the derived center pair
$(\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA), \cA)$ carries the
$\SCchtop$-algebra structure encoding both closed and open colours;
and $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ is the universal bulk
(Volume~II).

The bar complex thus organises five mathematical structures as
projections of one object: the genus expansion
$F_g=\kappa\cdot\lambda_g^{\mathrm{FP}}$ \textsc{(uniform-weight)} is
a GUE matrix model at $N^2=\kappa$; the ordered bar
$\barB^{\mathrm{ord}}(\cA)$ produces $U_q(\mathfrak g)$ via FRT
reconstruction; the quantum-group $R$-matrix yields knot invariants;
the shadow metric $Q_L$ defines a Bridgeland stability condition with
universal wall phase $\pi/4$; and the Stokes constants
$S_n/S_1=(-1)^{n+1}n$ encode the resurgent structure.

\medskip
\noindent\textbf{Corollary} (MC replaces the sum over topologies).
On the Koszul locus, the tree-level complex carries a contracting
homotopy (from the PBW degeneration), so $\Theta^{(g)}$ is determined
up to gauge-equivalent MC elements by induction from $\Theta^{(0)}$.
No free parameters appear at any genus; distinct choices of
contracting homotopy yield gauge-equivalent MC elements; no choice of
bulk topologies is required. The genus expansion is computed
algebraically from the genus-$0$ chiral bracket by the clutching
recursion of \S4.6, not approximated perturbatively. The
Maloney--Witten problem (negative Fourier coefficients in the
Poincar\'e series) does not arise: the MC equation determines each
$F_g$ uniquely by algebraic induction, without summing over bulk
topologies at fixed genus. The non-perturbative sum over distinct
three-manifold topologies lies outside the MC framework.


% ====================================================================
\section*{5.\quad The modular tangent complex and Chern--Weil theory}
% ====================================================================

The MC element $\Theta_\cA$ exists unconditionally and satisfies the
MC equation. Its deformation theory is controlled by the modular
tangent complex, obtained by twisting the convolution algebra by
$\Theta_\cA$ itself.

\subsection*{5.1.\enspace The $L_\infty$-twisted differential}

The MC element twists the convolution differential. For $x\in\gAmod$,
\[
d_{\Theta_\cA}(x):=\sum_{n\ge 0}\sum_{g\ge 0}\frac{\hbar^g}{n!}\ell_{n+1}^{(g)}(\Theta_\cA^{\otimes n},x)=d(x)+[\Theta_\cA,x]+\tfrac{1}{2!}\ell_3^{(0)}(\Theta_\cA,\Theta_\cA,x)+\hbar\ell_1^{(1)}(x)+\cdots
\]
In the strict chart this collapses to $d_{\Theta_\cA}(x)=d(x)+[\Theta_\cA,x]$.
The identity $d_{\Theta_\cA}^2=0$ is the MC equation for $\Theta_\cA$.

\subsection*{5.2.\enspace The modular tangent complex}

The \emph{modular tangent complex at $\Theta_\cA$}:
\[
T^{\mathrm{mod}}_{\Theta_\cA}:=(\gAmod,d_{\Theta_\cA}).
\]
Its cohomology governs deformations: $H^0$ infinitesimal automorphisms
(stabiliser), $H^1$ first-order deformations (tangent space), $H^2$
obstructions. $H^2=0$ makes the MC moduli smooth at $\Theta_\cA$;
$H^1=0$ makes $\Theta_\cA$ rigid.

For a one-parameter family $\cA_t$ varying in $k(t)$ or $c(t)$, the
tangent complex forms a local system over the parameter space and
the obstruction class traces a path in $H^2$. The vanishing locus
is the moduli of liftable deformations.

\medskip
\noindent\textbf{Tangent cohomology: Heisenberg.}\enspace
For $\cH_k$, the MC element $\Theta_{\cH_k}=k\cdot\eta\otimes\Lambda$
is a scalar, so the twisted differential $d_{\Theta}(x)=d(x)+[k\eta\Lambda,x]$
acts on the (abelian) convolution algebra with vanishing bracket.
The tangent complex reduces to the untwisted convolution complex:
$H^0(T^{\mathrm{mod}}_{\Theta_{\cH_k}})=\Bbbk$ (the identity
automorphism),
$H^1=\Bbbk$ (the tangent direction $\partial/\partial k$),
$H^2=0$ (no obstructions). The MC moduli is smooth and
one-dimensional: the level~$k$ is a free parameter with no
obstruction to deformation.

\medskip
\noindent\textbf{Tangent cohomology: Virasoro.}\enspace
For $\Vir_c$, the tangent complex is nontrivial. The twisted
differential $d_\Theta$ acts on the one-dimensional bar cohomology
spanned by the class $x$ dual to $T$. The tangent cohomology
$H^1(T^{\mathrm{mod}}_{\Theta_{\Vir_c}})$ is one-dimensional
(the direction $\partial/\partial c$). At $c=0$ and $c=-22/5$
the quartic contact invariant $Q^{\mathrm{contact}}=10/[c(5c+22)]$
has poles; these are \emph{not} singularities of the tangent complex
itself (which is well-defined for all $c$) but singularities of the
shadow projection. The tangent complex detects: the central charge
$c$ is a free deformation parameter; the shadow invariants $S_r$ are
\emph{not} independent deformation parameters but are algebraically
determined functions of $c$.

\medskip
\noindent\textbf{Tangent cohomology: affine KM at critical level.}\enspace
At the critical level $k=-h^\vee$, the tangent complex undergoes a
jump discontinuity. The curvature $\kappa=0$ means the MC element
is uncurved; the tangent cohomology $H^1$ doubles in dimension
(from $1$ at generic~$k$ to $1+\dim\mathfrak z(\widehat\fg_{-h^\vee})$
at critical level). The additional tangent directions correspond to
the Feigin--Frenkel center: the deformation theory at $k=-h^\vee$
sees the space of opers.

\subsection*{5.3.\enspace Three characteristic projections}

Three successive projections of $\Theta_\cA$ capture progressively
finer structure: $\kappa(\cA)$ (leading scalar curvature),
$\Delta_\cA(x)$ (characteristic polynomial of a finite-rank operator),
$\mathfrak R^{\mathrm{mod}}_4(\cA)$ (first nonlinear characteristic
class).

\medskip
\noindent\textbf{The scalar curvature.}\enspace
\[
\kappa(\cA)=\operatorname{tr}(\Theta_\cA)_{2,0}=\operatorname{tr}(\pi\circ m_2\circ\iota^{\otimes 2}\circ\Delta_{\mathrm{sep}})\in\Bbbk.
\]
This is the first Chern class of the modular bar bundle:
$\operatorname{obs}_g(\cA)=\kappa(\cA)\cdot\lambda_g$
\textsc{(uniform-weight)}; multi-weight at $g\ge 2$ adds
$\delta F_g^{\mathrm{cross}}$ \textsc{(all-weight)}. The Mumford relation
$\lambda_g^{g+1}=0$ confines genus-$g$ scalar obstructions to
dimension at most~$g$.

Explicit values across the standard landscape:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lccl}
\textbf{Algebra $\cA$} & $\kappa(\cA)$ & $\kappa(\cA^!)$ & \textbf{Sum rule}\\
\hline
Heisenberg $\cH_k$ & $k$ & $-k$ & $0$\\[1pt]
Affine $\widehat{\fg}_k$ & $\tfrac{(k+h^\vee)\dim\fg}{2h^\vee}$ & $-\tfrac{(k+h^\vee)\dim\fg}{2h^\vee}$ & $0$\\[4pt]
Virasoro $\mathrm{Vir}_c$ & $c/2$ & $(26-c)/2$ & $13$\\[1pt]
$\beta\gamma$ system ($\lambda{=}1$) & $1$ & $-1$ & $0$\\[1pt]
Lattice $V_\Lambda$ & $\operatorname{rank}(\Lambda)$ & $-\operatorname{rank}(\Lambda)$ & $0$\\[1pt]
$\mathcal W_N(\widehat{\mathfrak{sl}}_N)$ & $c\cdot(H_N-1)$ & $c'\cdot(H_N-1)$ & $K_N\cdot(H_N-1)$\\[4pt]
Free fermion $\psi$ & $1/4$ & $-1/4$ & $0$
\end{tabular}
\end{center}
$H_N=\sum_{j=1}^N 1/j$ is the harmonic number
($H_N-1\neq H_{N-1}$: at $N=2$, $H_2-1=1/2$ but $H_1=1$). The sum rule
$\kappa(\cA)+\kappa(\cA^!)=0$ holds for Kac--Moody, free fields,
lattice algebras. For $\mathcal W$-algebras the sum is a nonzero
constant: $\kappa(\mathrm{Vir}_c)+\kappa(\mathrm{Vir}_{26-c})=13$ and
$\kappa(\mathcal W_{N,c})+\kappa(\mathcal W_{N,c'})=K_N(H_N-1)$ with
$K_N=c+c'$. Self-duality occurs at $c=13$ for Virasoro and $c=50$
for $\mathcal W_3$.

\medskip
\noindent\textbf{The spectral discriminant.}\enspace
The Koszul dual Hilbert series
\[
h_{\cA^!}(q)=\sum_{n\ge 0}\dim H^n(\barB(\cA))\,q^n
\]
is rational for every standard family: it satisfies a holonomic
recurrence of finite order $d$, and the transfer matrix
$T_{\mathrm{rec}}$ is a $d\times d$ matrix. Define the
\emph{spectral branch object} as a finite-rank perfect complex
$V^{\mathrm{br}}_\cA$ with \emph{branch transport operator}
$T_{\mathrm{br},\cA}\colon V^{\mathrm{br}}_\cA\to V^{\mathrm{br}}_\cA$
and
\begin{equation}\label{eq:pref-delta-def}
\Delta_\cA(x):=\operatorname{sdet}(1-xT_{\mathrm{br},\cA}).
\end{equation}
The rank of $V^{\mathrm{br}}_\cA$ equals the degree of algebraicity of
$h_{\cA^!}$. Three properties: $\Delta_\cA$ is self-dual
($\Delta_{\cA^!}=\Delta_\cA$), unlike $\kappa$ which is anti-symmetric
for KM/free; exact factorization functors preserving quadratic OPE
data preserve $T_{\mathrm{br}}$; the spectral radius equals
$\dim\mathfrak g$ for affine KM at generic level.

\medskip
\noindent\textbf{Spectral discriminant: family-by-family.}\enspace
The spectral discriminant is computed explicitly for each standard
family:

\emph{Heisenberg $\cH_k$}: the bar cohomology is
$H^*(\barB(\cH_k))=\Bbbk\oplus\Bbbk\cdot x$ (two-dimensional,
concentrated in degrees $0$ and $1$). The Hilbert series is
$h(q)=1+q$, which is polynomial (degree of algebraicity $0$).
The transfer matrix is trivial: $T_{\mathrm{br}}=0$, and
$\Delta_{\cH_k}(x)=1$. The spectral discriminant carries no data
beyond $\kappa$. This is the Gaussian archetype: the second
characteristic projection is trivial.

\emph{$\beta\gamma$ system}: the bar cohomology has Hilbert series
$h(q)=\sqrt{(1+q)/(1-3q)}$, algebraic of degree~$2$. The branch
transport operator is a $2\times 2$ matrix with eigenvalues $3$ and
$-1$, giving $\Delta_{\beta\gamma}(x)=(1-3x)(1+x)$. The two roots
$x=1/3$ and $x=-1$ are the branch points of the algebraic function
$h(q)$. The spectral radius is $3$ (the larger eigenvalue); the
spectral gap is $3/1=3$.

\emph{Affine $\fsl_2$}: the bar cohomology dimensions grow as
$\dim H^n(\barB(\widehat{\fsl}_{2,k}))=\binom{n+2}{2}$ at generic
level, and $h(q)=1/(1-q)^3$ (rational, degree of algebraicity~$3$).
The transfer matrix eigenvalues are $1,1,1$ (all equal), and
$\Delta_{\widehat{\fsl}_2}(x)=(1-x)^3$. The spectral radius is $1$;
the degenerate eigenvalue structure reflects the $\fsl_2$ Weyl group
symmetry.

For $\mathfrak{sl}_3$: the degree-$3$ recurrence has transfer matrix
eigenvalues $8$, $(3\pm\sqrt{13})/2$, and
$\Delta_{\widehat{\mathfrak{sl}}_3}(x)=(1-8x)(1-3x-x^2)$. For
Heisenberg: $h_{\mathcal H_k^!}(q)=1+q$ and $\Delta_{\mathcal H_k}(x)=1$.
For $\beta\gamma$: $h=\sqrt{(1+q)/(1-3q)}$ and
$\Delta_{\beta\gamma}(x)=(1-3x)(1+x)$.

In the Chern--Weil dictionary, $\Delta_\cA$ plays the role of the
Chern character:
$\operatorname{ch}_r(\cA)=\tfrac{1}{r!}\tfrac{d^r}{dt^r}|_{t=0}[-\log\Delta_\cA(t)]=\tfrac{1}{r}\operatorname{tr}(T_{\mathrm{br}}^r)$.

\medskip
\noindent\textbf{The quartic shadow.}\enspace
\[
\mathfrak R^{\mathrm{mod}}_{4,g,n}(\cA)=\operatorname{pr}_{4,g,n}(\Theta_\cA)\in H^*(\overline{\cM}_{g,n})\otimes(\bar\cA^\vee)^{\otimes n}_{\mathrm{cyc}}.
\]
This is the first \emph{nonlinear} characteristic class: the first
invariant not recoverable from $\kappa$ and $\Delta_\cA$. Its
genus-zero, four-point specialisation is the quartic contact invariant
\[
Q^{\mathrm{contact}}_{\mathrm{Vir}}=\frac{10}{c(5c+22)},\qquad Q^{\mathrm{contact}}_{\cH}=0,\qquad Q^{\mathrm{contact}}_{\beta\gamma}\neq 0.
\]
(Verify: at $c=1$,
$Q_{\mathrm{Vir}}=10/27$.) For Heisenberg the
quartic vanishes (no cubic OPE pole). For $\beta\gamma$ the quartic
is the first gauge-nontrivial shadow (the cubic is gauge-removable).
For Virasoro, both cubic and quartic are nonvanishing.

\subsection*{5.4.\enspace The Chern--Weil dictionary}

The analogy between $\Theta_\cA$ and a connection $1$-form is exact.
The modular bar bundle
$\mathrm B^{\log}_{\mathrm{mod}}(\cA)\to\overline{\cM}_{g,n}$ is a
principal bundle for the gauge group of the convolution algebra;
$\Theta_\cA$ is its flat connection (flatness automatic); the shadow
tower is its Chern--Weil theory. Holonomy becomes factorisation
homology, gauge equivalence becomes MC gauge, and the Weil
homomorphism becomes the shadow algebra
$\cA^{\mathrm{sh}}=H_\bullet(\Defcyc^{\mathrm{mod}})$.

\begin{center}
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{ll}
\textbf{Classical Chern--Weil} & \textbf{Modular factorization}\\
\hline
Principal $G$-bundle $P\to M$ & Modular bar bundle $\mathrm B^{\log}_{\mathrm{mod}}(\cA)\to\overline{\cM}_{g,n}$\\[1pt]
Connection $\omega\in\Omega^1(P,\fg)$ & MC element $\Theta_\cA\in\operatorname{MC}(\gAmod)$\\[1pt]
Curvature $\Omega=d\omega+\tfrac12[\omega,\omega]$ & $D\Theta_\cA+\tfrac12[\Theta_\cA,\Theta_\cA]=0$\\[1pt]
Flatness $\Omega=0$ & Automatic (bar-intrinsic)\\[1pt]
First Chern $c_1$ & $\kappa(\cA)=\operatorname{tr}(\Theta_\cA)_{2,0}$\\[1pt]
Chern character & Spectral discriminant $\Delta_\cA(t)$\\[1pt]
Higher Chern classes $c_r$ & Shadows $\mathfrak R^{\mathrm{mod}}_{4,g,n}$, $\operatorname{Sh}_r$ ($r\ge 5$)\\[1pt]
Weil homomorphism & Shadow algebra $\cA^{\mathrm{sh}}=H_\bullet(\Defcyc^{\mathrm{mod}})$\\[1pt]
$\operatorname{ad}$-invariant polynomial & Cyclic cocycle in $\Defcyc^{\mathrm{mod}}(\cA)$\\[1pt]
Cyclic pairing $\operatorname{tr}(XY)$ & Verdier duality on $\operatorname{Ran}(X)$\\[1pt]
Group multiplication & Operadic composition in $\cP^{\mathrm{ch}}$\\[1pt]
Coproduct on $\cO(G)$ & Operadic cocomposition / clutching\\[1pt]
Lagrangian splitting $T^*G=\fg\oplus\fg^*$ & Complementarity $Q_g(\cA)\oplus Q_g(\cA^!)$\\[1pt]
Holonomy $\operatorname{Hol}(\gamma)$ & Factorisation homology $\int_\Sigma\cA$\\[1pt]
Gauge equivalence & MC gauge in $\operatorname{MC}_\bullet(\gAmod)$\\[1pt]
Transgression $\operatorname{CS}(\omega)$ & Shadow obstruction tower (\S6)\\[1pt]
Flat sections $\nabla s=0$ & Twisted cochains $d_{\Theta_\cA}(x)=0$
\end{tabular}
\end{center}

\medskip
\noindent\textbf{The Chern--Weil dictionary in practice.}\enspace
The table above is not merely an analogy: each entry is a precise
mathematical identification. Three examples:

\emph{Scalar curvature = first Chern class}: the classical first
Chern class $c_1(P)=\tfrac{1}{2\pi i}\mathrm{tr}(\Omega)$ computes
the curvature of a line bundle. The modular analogue: $\kappa(\cA)$
is the scalar curvature of the modular bar bundle, computed as
$\mathrm{tr}(\Theta_\cA)_{2,0}$. The Hodge class $\lambda_g=c_g(\mathbb E)$
plays the role of the Chern class polynomial.

\emph{Flatness = MC equation}: a connection is flat iff
$\Omega=d\omega+\tfrac12[\omega,\omega]=0$. The MC element
$\Theta_\cA$ satisfies $D\Theta+\tfrac12[\Theta,\Theta]=0$
automatically (bar-intrinsic). In the Chern--Weil setting, flat
connections are rare; in the modular setting, flatness is
guaranteed. The modular bar bundle is always flat; the shadow
tower records the characteristic classes of this flat connection,
which are secondary (Chern--Simons-type), not primary.

\emph{Holonomy = factorisation homology}: the holonomy of a flat
connection around a loop $\gamma$ is a group element
$\mathrm{Hol}(\gamma)\in G$. The modular analogue: the factorisation
homology $\int_\Sigma\cA$ of the chiral algebra over a surface
$\Sigma$ is the ``holonomy'' of the modular bar bundle around the
surface. For a closed surface of genus~$g$: the factorisation
homology computes the genus-$g$ conformal blocks; the MC projection
to genus~$g$ is the shadow of this computation.

\subsection*{5.5.\enspace The genus spectral sequence}

The genus filtration $F^g L_{\mathrm{mod}}:=\bigoplus_{g'\ge g}(\gAmod)_{g',*,*}$
yields a convergent spectral sequence. Write
$D_0=D_{\mathrm{int}}+D_{\mathrm{sep}}$ for the genus-preserving part
and $D_1=D_{\mathrm{nsep}}$ for the genus-raising part; these satisfy
$D_0^2=0$, $\{D_0,D_1\}=0$, $D_1^2=0$ (a bicomplex).

The spectral sequence: $E_0^{p,q}=\operatorname{gr}_F^p L_{\mathrm{mod}}^{p+q}$
with $d_0=[D_0,-]$; $E_1^{p,*}$ is the associated graded cohomology,
genus by genus; the differential $d_r$ at page $r$ encodes the
obstruction $\operatorname{Ob}_r$; $E_\infty^{p,q}\cong\operatorname{gr}_F^p H^{p+q}(L_{\mathrm{mod}})$.
Convergence follows from completeness of the depth filtration and
pronilpotence of the weight filtration; the $\varprojlim^1$ term
vanishes by Mittag-Leffler.

This spectral sequence is distinct from the PBW spectral sequence
(which decomposes by conformal weight within fixed genus). PBW
computes \emph{what} bar cohomology is; the genus spectral sequence
determines \emph{whether} the MC element extends across genera. For
Heisenberg it degenerates at $E_1$. For Virasoro, $d_1\neq 0$ and
nontrivial differentials persist at every page.

\medskip
\noindent\textbf{Heisenberg: $E_1$-degeneration.}\enspace
For $\cH_k$, the genus-preserving differential $D_0$ acts on each
genus-$g$ stratum independently. The genus-raising differential
$D_1$ is the BV operator $\hbar\Delta$. Because the convolution
bracket of $\cH_k$ is abelian, $D_1$ acts by scalar multiplication:
$\Delta(\Theta^{(g)})=\kappa\cdot\Theta^{(g+1)}$ (the genus loop
operator contracts two legs of a genus-$g$ amplitude and produces
a genus-$(g+1)$ amplitude). The $E_1$ page is one-dimensional at
each genus, generated by $\kappa^g\cdot[\lambda_g]$
\textsc{(uniform-weight)}. The differential $d_1$ on the $E_1$ page
vanishes because there is no room: the target $E_1^{g+1,*}$ is
generated by $\kappa^{g+1}\cdot[\lambda_{g+1}]$, and the map
$d_1\colon\kappa^g[\lambda_g]\mapsto 0$ by degree counting
(the BV operator lowers degree by~$2$, and
$\dim\overline{\cM}_g=3g-3$, so the degree mismatch forces
$d_1=0$). The spectral sequence degenerates at $E_1$: the full
cohomology is the direct sum of the genus-by-genus contributions.

\medskip
\noindent\textbf{Affine KM: $E_2$-degeneration.}\enspace
For $\widehat\fg_k$, the $E_1$ page is nontrivial at each genus
(the convolution bracket is nonabelian), and the differential
$d_1\neq 0$. However, the Jacobi identity on $\fg$ implies that
$d_2=0$: the quartic shadow vanishes ($S_4=0$), and the obstruction
to extending the MC element from the $E_1$ page to $E_2$ is trivial.
The spectral sequence degenerates at $E_2$. For $\fsl_2$ at level $k=1$:
the $E_1^{1,*}$ page has dimension $4$; the differential $d_1$
reduces this to dimension $2$ at $E_2^{1,*}$; then $d_r=0$ for all
$r\ge 2$.

\medskip
\noindent\textbf{Virasoro: non-degeneration.}\enspace
For $\Vir_c$, the spectral sequence does not degenerate at any finite
page. The differentials $d_r$ are nonzero for infinitely many $r$,
reflecting the infinite shadow depth. At each page, the quartic
contact invariant and its descendants produce nontrivial
differentials. The $E_\infty$ page is computed by the full infinite
tower; no finite truncation suffices.

\subsection*{5.6.\enspace Homotopy invariance and functoriality}

The shadow algebra $\cA^{\mathrm{sh}}=H_\bullet(\Defcyc^{\mathrm{mod}}(\cA))$
is a homotopy invariant. For any $\infty_\alpha$-quasi-isomorphism
$f\colon\cA\xrightarrow{\sim}\cA'$,
\[
f_*\colon\operatorname{MC}_\bullet(\gAmod)\xrightarrow{\;\sim\;}\operatorname{MC}_\bullet(\mathfrak g^{\mathrm{mod}}_{\cA'})
\]
is a weak homotopy equivalence. The scalar $\kappa$, the spectral
determinant $\Delta_\cA$, and the full shadow obstruction tower
$(\kappa,\Delta,\mathfrak C,\mathfrak Q,\operatorname{Sh}_5,\ldots)$
consist of quasi-isomorphism invariants; $\Theta_\cA$ itself is a
quasi-isomorphism invariant up to gauge. The assignment
$\cA\mapsto(\gAmod,\Theta_\cA)$ is a functor from chiral algebras with
$\infty_\alpha$-quasi-isos inverted to MC moduli problems. The
convolution $L_\infty$-algebra is functorial in each slot separately
but not as a bifunctor; functoriality of $\cA\mapsto\gAmod$ proceeds
through the source slot.

\subsection*{5.7.\enspace The shadow CohFT and topological recursion}

Projected to $\overline{\cM}_{g,n}$, the MC equation produces
tautological classes and tautological relations. The MC element
determines shadow tautological classes
$\tau_{g,n}(\cA)\in R^*(\overline{\cM}_{g,n+1})$ assembling into a
cohomological field theory (Theorem~\ref{thm:shadow-cohft}): the
factorisation axiom holds by the clutching law, the
$\Sigma_n$-equivariance by the symmetry of stable-graph summation,
the flat identity conditionally on the vacuum lying in~$V$.

Projecting the MC equation to the $(g,n)$-component yields a
tautological relation in $R^*(\overline{\cM}_{g,n})$ at each $(g,n)$:
\[
\sum_{\mathrm{sep}/\mathrm{nsep}}\xi_{\mathrm{sep},*}\bigl(\tau_{g_1,|S|}(\cA)\cdot\tau_{g_2,|S^c|}(\cA)\bigr)+\delta_{\mathrm{pf}}^{(g,n)}=0.
\]

\medskip
\noindent\textbf{WDVV and Mumford from MC.}\enspace
At genus~$0$, degree~$3$: the MC tautological relation on
$\overline{\cM}_{0,4}$ reduces to WDVV. At degree~$2$, genus~$g\ge 2$:
substituting $\tau_{g,2}(\cA)=\kappa\cdot\pi^*\lambda_g$
\textsc{(uniform-weight)} recovers the Mumford $\lambda$-class
clutching relation on $\overline{\cM}_g$.

The complementarity propagator
$P_\cA\colon H^*(\cA)\otimes H^*(\cA^!)\to\mathbb C$ is the Givental
$R$-matrix of the shadow CohFT; when it carries a flat unit (all
standard families with vacuum in $V$), Teleman reconstruction
recovers $\{\tau_{g,n}\}$ at all $(g,n)$ from genus-$0$ data and
$P_\cA$. Eynard--Orantin topological recursion is the MC equation
applied to the shadow obstruction tower.

\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{ll}
\textbf{MC datum} & \textbf{Tautological output}\\
\hline
$\Theta_\cA\in\operatorname{MC}(\gAmod)$ & shadow CohFT $\Omega_{g,n}^\cA$\\[1pt]
$D^2=0$ on $\mathrm{FM}^{\log}$ & CohFT axioms\\[1pt]
$D\Theta+\tfrac12[\Theta,\Theta]=0$ at $(g,n)$ & tautological relation\\[1pt]
$[\Theta,\Theta]|_{\mathrm{sep}}$ & WDVV / associativity\\[1pt]
$\hbar\Delta(\Theta)|_{\mathrm{nsep}}$ & Mumford $\lambda$-class relations\\[1pt]
$P_\cA$ & Givental $R$-matrix\\[1pt]
MC recursion & EO topological recursion
\end{tabular}
\end{center}

\medskip
\noindent\textbf{The Pixton shadow bridge.}\enspace
For class-M algebras, $\Theta_\cA$ generates tautological classes at
every genus. At genus~$2$--$3$, the relations
$\tau_{g,n}(\mathrm{Vir}_c)$ for generic $c$ produce elements of the
Pixton ideal in $R^*(\overline{\cM}_{g,n})$: Pixton's tautological
ring relations arise as shadows of the Virasoro MC equation. On the
semisimple locus, MC-descended relations together with Mumford
relations generate the Pixton ideal
(Theorem~\ref{thm:pixton-from-mc-semisimple}); the non-semisimple
frontier remains open.

\medskip
\noindent\textbf{Pixton relations from MC: the mechanism.}\enspace
The MC equation at $(g,n)$ produces a tautological relation in
$R^*(\overline{\cM}_{g,n})$ because each term in the MC equation
is a pushforward of a boundary class. At genus~$2$, $n=0$:
the MC relation involves three terms (iterated BV, clutching-times-BV,
planted-forest) as in the genus-$2$ shell table of \S6.7. For
Virasoro at generic~$c$, these three terms are nonzero and produce a
nontrivial relation in $R^2(\overline{\cM}_2)$: the Pixton relation
$\kappa_1^2-12\lambda_1\kappa_1+48\lambda_1^2=0$ (in the notation
of the tautological ring). The class-M property guarantees that the
relation is nontrivial: if the tower terminated, the relation would
be vacuous. The Pixton relations are shadows of the infinite tower.

At genus~$3$: the MC equation at $(3,0)$ involves five stable graph
types and produces relations in $R^3(\overline{\cM}_3)$. These
reproduce the Faber--Zagier relations, which are known to generate
the Pixton ideal at $g=3$. At higher genus, the MC-descended
relations become progressively more complex but always land in the
Pixton ideal by the semisimplicity theorem.

\medskip
\noindent\textbf{The Eynard--Orantin connection.}\enspace
Eynard--Orantin topological recursion computes the correlators
$\omega_{g,n}(z_1,\ldots,z_n)$ of a spectral curve from the
genus-$0$ two-point function $\omega_{0,2}$ and the Bergman kernel.
In the MC framework, the spectral curve is the shadow metric $Q_L(t)$
of~\eqref{eq:preface-riccati-hook}, the Bergman kernel is the
complementarity propagator $P_\cA$, and the recursion kernel is the
MC clutching law. The correspondence is:
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{ll}
\textbf{Eynard--Orantin} & \textbf{MC framework}\\
\hline
Spectral curve $(C,x,y)$ & Shadow metric $(L,Q_L,H)$\\[1pt]
Bergman kernel $B(z_1,z_2)$ & Complementarity propagator $P_\cA$\\[1pt]
Recursion kernel $K(z_0,z)$ & MC clutching law at $(g,n)$\\[1pt]
Branch points & Zeros of $Q_L$: $\Delta=0$ locus\\[1pt]
Residue at branch point & Shadow obstruction class $o_{r+1}$\\[1pt]
Free energy $F_g$ & Shadow amplitude $F_g=\kappa\cdot\lambda_g^{\mathrm{FP}}$ \textsc{(uniform-weight)}
\end{tabular}
\end{center}
The recursion is the MC equation projected to fixed $(g,n)$ and
restricted to the primary line $L$. For class-G algebras, the
spectral curve is rational and the recursion terminates. For
class-M algebras, the spectral curve is hyperelliptic (the algebraic
curve $y^2=Q_L(t)$ of degree~$2$) and the recursion produces an
infinite family of correlators. This identification is exact on the
semisimple locus (where $\Delta\neq 0$); the non-semisimple locus
$\Delta=0$ requires a separate analysis.

\medskip
\noindent\textbf{The B\"ocherer bridge.}\enspace
At genus~$2$, the shadow tautological class $\tau_{2,0}(\mathrm{Vir}_c)$
for lattice vertex algebras computes a central $L$-value via the
B\"ocherer conjecture (Furusawa--Morimoto). For the Leech lattice,
$\chi_{12}=\operatorname{SK}(f_{22})$, and the MC-derived second
Fourier coefficient $c_2\approx-1.918\times 10^{-6}\neq 0$ is the
first nonzero central $L$-value produced by the shadow obstruction
tower.

\subsection*{5.8.\enspace The primitive kernel and cofree reduction}

$\Theta_\cA$ lives in the cofree conilpotent coalgebra underlying the
modular bar construction. By Milnor--Moore for modular operads,
$\Theta_\cA$ is determined by its restriction to primitive corollas
and rigid cutting strata, the \emph{primitive logarithmic modular
kernel}
\[
\mathfrak K_\cA=\sum_{g\ge 0,n\ge 2}K_{g,n}^\cA+\sum_{\rho\in\mathrm{Rig}}K_\rho^\cA,
\]
and the equivalence (Theorem~\ref{thm:primitive-to-global-reconstruction})
\[
(Q_\cA^{\mathrm{mod}})^2=0\iff d\mathfrak K_\cA+\mathfrak K_\cA\star\mathfrak K_\cA+\hbar\Delta_{\mathrm{ns}}(\mathfrak K_\cA)=0,
\]
with $\star$ the primitive pre-Lie product from log-FM residues,
replaces the genus-by-genus obstruction programme by a single equation
on primitive data.

\medskip
\noindent\textbf{Shell equations.}\enspace
Projecting to genus~$2$ and~$3$:
\begin{align*}
R_2(\mathfrak K_\cA)&=\Delta_{\mathrm{ns}}(K_1)+\tfrac12[K_1,K_1]+\sum_{\rho\in\mathrm{Rig}_2}R_\rho^\cA(K_{0,2}^\cA),\\
R_3(\mathfrak K_\cA)&=\Delta_{\mathrm{ns}}(K_2)+[K_1,K_2]+\tfrac{1}{3!}\ell_3(K_1,K_1,K_1)+\sum_\rho R_\rho^\cA(\ldots).
\end{align*}
For Heisenberg, only $\Delta_{\mathrm{ns}}$ survives. For affine
Kac--Moody, $[K_1,K_1]$ contributes the cubic shadow. For
$\beta\gamma$, cubic gauge triviality kills the bracket and the rigid
stratum contributes the quartic contact invariant. For Virasoro and
$\mathcal W_N$, all three terms are active at every genus.

\medskip
\noindent\textbf{The branch BV action.}\enspace
The finite-rank branch-active quotient
$V_\cA^{\mathrm{br}}=V_\cA^+\oplus V_\cA^-$ carries a BV master action
\[
S_\cA^{\mathrm{br}}(x,\xi)=\tfrac12\Omega_\cA(K_\cA^{\mathrm{br}}x,x)+\sum_{m+n\ge 3}\frac{1}{m!n!}\mu_{m,n}^\cA(x^{\otimes m};\xi^{\otimes n}),
\]
satisfying
$\hbar\Delta_\cA^{\mathrm{br}}S_\cA^{\mathrm{br}}+\tfrac12\{S_\cA^{\mathrm{br}},S_\cA^{\mathrm{br}}\}_{\mathrm{BV}}=0$.
The metaplectic half-density $\delta_\cA\in 1+x\Bbbk[[x]]$ satisfies
$\delta_\cA^2=\Delta_\cA=\det(1-xT_\cA^{\mathrm{br,red}})$: the
spectral discriminant is the square of a canonical half-density.

\medskip
\noindent\textbf{Shell equations: Heisenberg worked example.}\enspace
For $\cH_k$, the primitive kernel reduces to $\mathfrak K_{\cH_k}=K_1$
(genus~$1$, the BV operator applied once). The genus-$2$ shell:
$R_2=\Delta_{\mathrm{ns}}(K_1)=\Lambda_P(K_1)$, the genus loop
operator applied to the genus-$1$ amplitude. The bracket
$[K_1,K_1]=0$ (abelian) and the rigid stratum contribution is zero
(no higher shadows). So $R_2=\Lambda_P(\kappa\cdot\lambda_1)$.
The loop operator contracts two legs with the propagator $P=1/k$,
giving $R_2=k\cdot(1/k)\cdot\lambda_2=\lambda_2$ (a cohomology class
on $\overline{\cM}_2$). The genus-$3$ shell:
$R_3=\Delta_{\mathrm{ns}}(K_2)=\Lambda_P(R_2)=\lambda_3$. By
induction: $R_g=\lambda_g$ for all $g$, and
$F_g(\cH_k)=\kappa\cdot\lambda_g^{\mathrm{FP}}$
\textsc{(uniform-weight)}: the $\hat A$-genus is reproduced by
iterated BV alone.

\medskip
\noindent\textbf{Shell equations: affine KM worked example.}\enspace
For $\widehat{\fsl}_{2,k}$, the genus-$2$ shell has two nonzero
terms: $R_2=\Delta_{\mathrm{ns}}(K_1)+\tfrac12[K_1,K_1]$. The
bracket $[K_1,K_1]$ is nonzero (the Lie bracket of $\fsl_2$ via the
cubic shadow $S_3$), but the Jacobi identity forces
$\tfrac{1}{3!}\ell_3(K_1,K_1,K_1)=0$ at genus~$3$: the Lie bracket
contribution terminates. The genus-$2$ shell simplifies to
$R_2=\Lambda_P(\kappa\lambda_1)+\tfrac12\kappa S_3\cdot\lambda_2$,
and the result is $F_2=7\kappa/5760$ \textsc{(uniform-weight)}: the
scalar formula holds because $\fsl_2$ is uniform-weight (single
generator at conformal weight~$1$). The cubic shadow $S_3$ enters
the shell equation but cancels in the uniform-weight projection.

\subsection*{5.9.\enspace Entanglement from the modular characteristic}

The bar coalgebra carries a natural bipartite structure: its coproduct
splits a configuration of points into two halves, one on each side of
a spatial cut. For a spatial bipartition of an interval of length $L$
with UV cutoff $\varepsilon$, the scalar projection of $\Theta_\cA$
restricted to the bipartite cut yields
\[
S_{\mathrm{EE}}(\cA)=\frac{c(\cA)}{3}\log\frac{L}{\varepsilon}.
\]
For Virasoro $c=2\kappa$; the relationship between $c$ and $\kappa$
is family-dependent. Complementarity gives the entanglement sum rule
$S_{\mathrm{EE}}(\cA)+S_{\mathrm{EE}}(\cA^!)=\tfrac{c(\cA)+c(\cA^!)}{3}\log(L/\varepsilon)$;
for the Virasoro family $\mathrm{Vir}_c^!=\mathrm{Vir}_{26-c}$ this
gives $c+c'=26$ and the universal sum $26/3\cdot\log(L/\varepsilon)$.

The four shadow-depth classes (G/L/C/M) classify entanglement
complexity: class G (Gaussian, $r_{\max}=2$) exhibits area-law
entanglement only; class L ($r_{\max}=3$) adds subleading logarithmic
corrections from the cubic shadow; class C ($r_{\max}=4$) adds a
contact correction from the quartic invariant; class M
($r_{\max}=\infty$) carries an infinite tower of corrections.

\medskip
\noindent\textbf{The entanglement programme (G11--G16).}\enspace
Six theorem targets extend the scalar result. G11: Ryu--Takayanagi
from the scalar projection of $\Theta_\cA$. G12: Koszulness as exact
quantum error correction; the Knill--Laflamme condition is the
Lagrangian isotropy condition from the complementarity pairing;
shadow depth equals the number of redundancy channels; the twelve
Koszulness characterisations translate into a twelve-fold code
dictionary; failure of Koszulness is failure of the code. G13:
replica trick from the MC equation. G14: modular flow from the
tangent complex. G15: QES as the shadow connection Ward identity.
G16: Page curve at $c=13$ from the shadow connection at the self-dual
point; the scrambling time is controlled by $\Delta_\cA$.


% ====================================================================
\section*{6.\quad The shadow obstruction tower}
% ====================================================================

\subsection*{6.1.\enspace The extension tower}

Can $\Theta_\cA$ be approximated by finitely many degrees, and what
controls the passage from one finite approximation to the next? The
total weight filtration answers both.

Define the \emph{total weight} $w(g,r,d):=2g-2+r+d$. The filtration
$F^N\mathfrak g^{\mathrm{amb}}_\cA:=\bigoplus_{w\ge N}(\mathfrak g^{\mathrm{amb}}_\cA)_{g,r,d}$
is exhaustive, separated, complete. $\mathfrak g^{\mathrm{amb}}_\cA$
is the \emph{ambient} (planted-forest-extended) modular convolution
algebra. The \emph{modular extension tower}:
\[
\cE_\cA(N):=\operatorname{MC}(\mathfrak g^{\mathrm{amb}}_\cA/F^{N+1}),\qquad N\ge 1,
\]
with restriction maps $\cE_\cA(N+1)\to\cE_\cA(N)$. A full lift is a
compatible point of the inverse system; the bar-intrinsic construction
provides one unconditionally. The shadow obstruction tower studies
$\cE_\cA(1)\leftarrow\cE_\cA(2)\leftarrow\cE_\cA(3)\leftarrow\cdots$.

\subsection*{6.2.\enspace Obstruction classes and the all-degree master equation}

Define $\Theta_\cA^{\le r}$ by projecting to total weight $\le r$. The
\emph{shadow obstruction tower} is the sequence
$\Theta_\cA^{\le 2},\Theta_\cA^{\le 3},\Theta_\cA^{\le 4},\ldots$ At
each truncation the MC equation fails by a remainder,
\[
D\Theta^{\le r}_\cA+\tfrac12[\Theta^{\le r}_\cA,\Theta^{\le r}_\cA]=-o_{r+1}(\cA),
\]
with obstruction class $o_{r+1}(\cA)\in Z^2(F^{r+1}/F^{r+2},d_{\le r})$.
Extension is possible iff $[o_{r+1}]=0$ in
$H^2(F^{r+1}/F^{r+2},d_{\le r})$. The bar-intrinsic construction
guarantees extension, so the obstruction class is always exact; the
shadow obstruction tower records the gauge choices at each stage.

The all-degree master equation at degree~$r$:
\[
\nabla_H(\operatorname{Sh}_r(\cA))+o^{(r)}(\cA)=0,\qquad r\ge 3,
\]
with $\nabla_H$ the Hodge covariant derivative. This equation
determines $\operatorname{Sh}_r$ uniquely modulo gauge if
$H^1(F^r/F^{r+1},d_{\le r-1})=0$.

\medskip
\noindent\textbf{Obstruction classes: explicit computation.}\enspace
The obstruction class $o_{r+1}$ at degree~$r+1$ has a concrete graph
formula:
\[
o_{r+1}(\cA)=\sum_{\substack{\Gamma\in\mathsf{Gr}^{\mathrm{st}}\\w(\Gamma)=r+1}}\frac{1}{|\Aut(\Gamma)|}\cdot\partial_\Gamma(\Phi_\cA^{\le r}),
\]
where $\partial_\Gamma$ is the boundary operator that contracts one
edge of $\Gamma$ and evaluates the amplitude on the contraction, and
$\Phi_\cA^{\le r}$ is the graph amplitude truncated to weight $\le r$.
The sum runs over all stable graphs of total weight $r+1$; at each
graph, the obstruction is the failure of the truncated amplitude to
satisfy the MC equation on that graph.

At degree~$3$: the obstruction $o_3(\cA)$ is the Jacobiator. It
lies in $H^2(\cA^{\mathrm{sh}}_{3,0})$, which for a Lie algebra
input is $H^2(\fg,\fg)$ (the Lie algebra cohomology governing
deformations). For $\widehat\fg_k$: $o_3=0$ because the Lie
bracket satisfies Jacobi. For $\Vir_c$: $o_3\neq 0$ but is
gauge-trivial (cubic gauge triviality, \S6.3 below).

At degree~$4$: the obstruction $o_4(\cA)$ is the quartic contact
invariant (after the cubic gauge is fixed). For $\widehat\fg_k$:
$o_4=0$ by Jacobi. For $\Vir_c$:
$o_4=10/[c(5c+22)]\neq 0$. For $\beta\gamma$: $o_4\neq 0$ (the
first nonvanishing obstruction, since $o_3=0$ for $\beta\gamma$).

At degree~$5$: the obstruction $o_5(\cA)=\{\mathfrak C,\mathfrak Q\}_H$
is the Poisson bracket of the cubic and quartic shadows. For
Virasoro: $o_5=480/[c^2(5c+22)]\cdot x^5\neq 0$ (\S6.9).

\subsection*{6.3.\enspace Cubic gauge triviality and the canonical quartic}

\begin{quote}
\textbf{Cubic gauge triviality.}\enspace
When $H^1(F^3/F^4,d_2)=0$, the cubic MC term $\Theta^{[3]}_\cA$ is
gauge-trivial: there exists $\exp(\xi_3)$ with $\xi_3\in F^3$ such that
$\exp(\xi_3)\cdot\Theta^{\le 3}_\cA$ has vanishing weight-$3$
component.
\end{quote}

After this gauge transformation, the quartic obstruction class
$[\mathfrak Q(\cA)]\in H^2(F^4/F^5,d_2)$ is canonical: independent of
homotopy retraction data, cubic gauge, and MC gauge orbit
representative. This is the first characteristic class not polynomial
in $\kappa$. The mechanism is standard Postnikov: trivial $H^1$ at
level $n$ makes the $H^2$ class at level $n+1$ canonical.

\medskip
\noindent\textbf{Cubic gauge triviality: proof.}\enspace
The obstruction to extending $\Theta^{\le 2}_\cA$ to degree~$3$
lies in $H^2(F^3/F^4,d_2)$. The bar-intrinsic construction provides
a specific extension (so the obstruction class is exact), but the
extension is not unique: two extensions differ by an element
$\xi_3\in\ker(d_2)\cap F^3/F^4=H^1(F^3/F^4,d_2)$. When
$H^1(F^3/F^4,d_2)=0$, the cubic extension is unique (up to
$d_2$-exact terms), and the exponential gauge action
$\exp(\xi_3)\cdot\Theta^{\le 3}$ has no gauge freedom at weight~$3$.
After fixing this gauge, the quartic class
$[\mathfrak Q]=[\Theta^{[4]}+\tfrac{1}{2}\{\Theta^{[3]},\Theta^{[3]}\}]$
is canonically determined.

The condition $H^1(F^3/F^4,d_2)=0$ holds for all standard families
on the Koszul locus. Off the Koszul locus (e.g., at the critical level
$k=-h^\vee$ for affine KM), $H^1$ may be nonzero and the quartic class
acquires a choice.

\medskip
\noindent\textbf{Family-by-family quartic invariant.}\enspace
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lcl}
\textbf{Algebra} & $Q^{\mathrm{contact}}$ & \textbf{Comment}\\
\hline
$\cH_k$ & $0$ & no cubic OPE pole\\
$\widehat\fg_k$ & $0$ & Jacobi kills quartic\\
$\beta\gamma$ & $\neq 0$ & first nontrivial shadow\\
$\Vir_c$ & $10/[c(5c{+}22)]$ & both cubic and quartic nonzero\\
$\cW_3$ & $\neq 0$ & DS-escalated from $\fsl_3$
\end{tabular}
\end{center}

The clutching law for the quartic follows from Mok's log FM
degeneration formula. For $C\leadsto C_0=C_1\cup_p C_2$,
\[
\mathfrak Q(\cA)|_{C_0}=\sum_{a+b=4}\mathfrak Q^{(a)}(\cA)|_{C_1}\cdot\mathfrak Q^{(b)}(\cA)|_{C_2}+\text{planted-forest correction}.
\]
The correction is genuinely logarithmic, with no DM counterpart.

The quartic contact invariant
$Q^{\mathrm{contact}}_{\mathrm{Vir}}=10/[c(5c+22)]\in H^2(F^4/F^5,d_2)$.
The denominator has physical meaning: $c=0$ is the logarithmic
threshold; $c=-22/5$ is the minimal model accumulation point
$\mathcal M(2,5)$. The numerator $10=\binom{5}{2}$ counts degree-four
Catalan channels.

\medskip
\noindent\textbf{Numerical values of the Virasoro quartic.}\enspace
\begin{center}
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{ccc}
$c$ & $Q^{\mathrm{contact}}_{\Vir}$ & \textbf{Significance}\\
\hline
$1$ & $10/27\approx 0.370$ & free boson Virasoro\\
$1/2$ & $10/(1/2\cdot 49/10)=200/49\approx 4.08$ & Ising model\\
$13$ & $10/(13\cdot 87)=10/1131\approx 0.00884$ & self-dual\\
$25$ & $10/(25\cdot 147)=10/3675\approx 0.00272$ & bosonic string\\
$26$ & $10/(26\cdot 152)=10/3952\approx 0.00253$ & critical string
\end{tabular}
\end{center}
The quartic decreases monotonically for $c>0$ and diverges as $c\to 0^+$
(logarithmic threshold) and $c\to(-22/5)^+$ (minimal model accumulation).

\subsection*{6.4.\enspace The Hamilton--Jacobi generating function}

For a multi-generator algebra ($\mathcal W_3$ with generators $T$
(weight~$2$) and $W$ (weight~$3$)), the deformation space is
two-dimensional. The Riccati ODE lifts to a Hamilton--Jacobi PDE.
Write $U=\sum_{s\ge 3}\operatorname{Sh}_s(x_T,x_W)$; the master equation
becomes
\[
2E(U)+\tfrac12\lVert\nabla U\rVert^2_H=R(x_T,x_W),
\]
with Euler operator $E=x_T\partial_T+x_W\partial_W$, kinetic energy
$\lVert\nabla U\rVert^2_H=(2/c)(\partial_T U)^2+(3/c)(\partial_W U)^2$,
and $R$ a polynomial of degree $\le 4$ in
$(\kappa,\mathfrak C,\mathfrak Q)$. The gradient $dU\colon X\to T^*X$
embeds the deformation space as a Lagrangian submanifold of $T^*X$.
Whether the genus expansion admits a quantisation with $U$ as leading
semiclassical term is open: it would require a quantum Hamiltonian
whose WKB expansion has leading term $U$ and whose quantum corrections
reproduce the genus-$g$ shadow amplitudes.

On the $T$-line the conformal weight forces the transverse momentum to
vanish and the PDE collapses to the Riccati ODE. On the $W$-line the
cubic shadow $\operatorname{Sh}_3=2x_T^3+3x_Tx_W^2$ has nonzero normal
derivative $(\partial_T\operatorname{Sh}_3)|_{x_T=0}=3x_W^2$, and the
first inter-channel coupling correction enters at degree~$6$:
\[
\delta_6^{W\text{-line}}=\frac{576(5c+38)}{c^3(5c+22)^3}.
\]
The $T$-line is autonomous; the $W$-line is not. The asymmetry is
intrinsic to the weight difference between $T$ (weight~$2$) and $W$
(weight~$3$).

\subsection*{6.5.\enspace The four depth classes}

The \emph{shadow depth} $r_{\max}(\cA)$ is the smallest $r$ such that
$o_{r+1}(\cA)=0$ for all subsequent levels, or $\infty$ if the tower
never terminates. The standard landscape partitions into four depth
classes; no other values occur on any one-dimensional primary slice.
The single-line dichotomy: the shadow metric $Q_L(t)$ is quadratic in
$(\kappa,\alpha,S_4)$, and its factorisation type (perfect square or
irreducible) determines whether the tower terminates.

\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lcccll}
\textbf{Class} & \textbf{Symbol} & $r_{\max}$ & $\ell_3^{(0)},\ell_4^{(0)}$ & \textbf{Potential} & \textbf{Examples}\\
\hline
Gaussian & G & $2$ & $0,0$ & quadratic & Heisenberg $\cH_k$, free fermion $\psi$\\
Lie/tree & L & $3$ & $\neq 0,0$ & cubic & Affine $\widehat{\mathfrak{sl}}_N$, currents\\
Contact & C & $4$ & $0,\neq 0$ & quartic & $\beta\gamma$, $bc$ ghosts\\
Mixed & M & $\infty$ & $\neq 0,\neq 0$ & non-polynomial & Virasoro, $\mathcal W_N$, $\mathcal W_\infty$
\end{tabular}
\end{center}

\noindent
\textbf{Gaussian} ($r_{\max}=2$): transferred brackets $\ell_k^{(0)}$
vanish for $k\ge 3$ on bar cohomology, so the tower terminates at
$\kappa$. Two mechanisms: Heisenberg has no simple pole; the free
fermion has a simple pole but fermionic antisymmetry forces $S_3=0$.
Sewing is by Fredholm determinant (Heisenberg) or Pfaffian (fermion).
\textbf{Lie/tree} ($r_{\max}=3$): the OPE has a simple pole generating
a Lie bracket, but $\ell_4^{(0)}$ vanishes on bar cohomology.
\textbf{Contact} ($r_{\max}=4$): the simple-pole bracket vanishes on
bar cohomology, but the quaternary bracket survives; the first
nontrivial shadow is $\mathfrak Q(\cA)$. \textbf{Mixed}
($r_{\max}=\infty$): both cubic and quartic shadows are nontrivial,
and their Poisson bracket $\{\mathfrak C,\mathfrak Q\}_H$ generates a
nonvanishing quintic, then sextic, and so on.

\medskip
\noindent\textbf{Shadow depth is not Koszulness.}\enspace
All four depth classes contain chirally Koszul algebras. Heisenberg
(depth~$2$), affine at generic level (depth~$3$), $\beta\gamma$
(depth~$4$), and Virasoro (depth~$\infty$) are all chirally Koszul.
Shadow depth classifies the complexity of Koszul algebras, not
Koszulness itself.

The \emph{operadic complexity theorem}
(Theorem~\ref{thm:operadic-complexity-detailed}):
\[
r_{\max}(\cA)=A_\infty\text{-depth}(\cA)=L_\infty\text{-formality level}(\cA).
\]
$A_\infty$-depth is the largest $r$ with $m_r\neq 0$ in the minimal
$A_\infty$ model; $L_\infty$-formality level is the largest $r$ with a
nontrivial $r$-ary bracket on bar cohomology not removable by
$L_\infty$-isomorphism.

\medskip
\noindent\textbf{The depth gap theorem.}\enspace
The algebraic depth $d_{\mathrm{alg}}(\cA)$ takes values in $\{0,1,2,\infty\}$;
the value $3$ is impossible. This is a structural constraint, not an
empirical observation. The proof:

At depth~$3$ in the shadow obstruction tower, the MC equation at
degree~$4$ reads
$d(S_4)+\tfrac{1}{2}\{S_3,S_3\}_H=0$. If $d_{\mathrm{alg}}=3$, then
$S_r=0$ for $r\ge 4$; in particular $S_4=0$. But the
Poisson bracket $\{S_3,S_3\}_H$ of the cubic shadow with itself is
computed by the shadow Lie algebra Jacobi identity:
$\{S_3,S_3\}_H=0$ iff the graded Jacobi identity holds on the
cubic shadow viewed as a Lie bracket on bar cohomology. For a genuine
Lie bracket (class~L), Jacobi holds, so $S_4=0$ and the tower
terminates at $r_{\max}=3$. For a bracket that is \emph{not}
Lie (violates Jacobi), $\{S_3,S_3\}_H\neq 0$ and $S_4\neq 0$,
forcing $d_{\mathrm{alg}}\ge 4$. The MC relation at degree~$5$
then forces $\{S_3,S_4\}_H\neq 0$ and the induction continues:
$d_{\mathrm{alg}}=\infty$.

The transition $3\to 4$ is impossible: if $S_3\neq 0$, then either
Jacobi kills $S_4$ (and the tower stops at $3$) or Jacobi fails and
the tower runs to $\infty$. The value $d_{\mathrm{alg}}=4$ requires
$S_3=0$ and $S_4\neq 0$, which is the contact class~C
($\beta\gamma$). The four values $\{0,1,2,\infty\}$ map to:
$0$=trivial, $1$=free field (linear differential), $2$=Gaussian
(class~G), $\infty$=mixed (class~M). The value $3$ would require a
non-Lie cubic shadow that magically satisfies Jacobi, which is a
contradiction.

\medskip
\noindent\textbf{Depth classification: extended table.}\enspace
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lcccccc}
\textbf{Algebra} & \textbf{Class} & $r_{\max}$ & $\kappa$ & $S_3$ & $S_4$ & $\Delta$\\
\hline
$\cH_k$ & G & $2$ & $k$ & $0$ & $0$ & $0$\\
Free fermion $\psi$ & G & $2$ & $1/4$ & $0$ & $0$ & $0$\\
$\widehat{\fsl}_{2,k}$ & L & $3$ & $3(k{+}2)/4$ & $\neq 0$ & $0$ & $0$\\
$\widehat{\fsl}_{3,k}$ & L & $3$ & $4(k{+}3)/3$ & $\neq 0$ & $0$ & $0$\\
$\beta\gamma$ ($\lambda{=}1$) & C & $4$ & $1$ & $0$ & $\neq 0$ & $\neq 0$\\
$bc$ ($\lambda{=}2$) & C & $4$ & $-26/2$ & $0$ & $\neq 0$ & $\neq 0$\\
$\Vir_c$ & M & $\infty$ & $c/2$ & $\neq 0$ & $10/[c(5c{+}22)]$ & $\neq 0$\\
$\cW_3$ & M & $\infty$ & $5c/6$ & $\neq 0$ & $\neq 0$ & $\neq 0$\\
$\cW_\infty$ & M & $\infty$ & $c/2$ & $\neq 0$ & $\neq 0$ & $\neq 0$
\end{tabular}
\end{center}
The discriminant $\Delta=8\kappa S_4$ controls the single-line
dichotomy: $\Delta=0$ forces finite tower termination;
$\Delta\neq 0$ forces an infinite tower. The discriminant is
\emph{linear} in $\kappa$ (not quadratic); for $\kappa\neq 0$,
$\Delta=0$ iff $S_4=0$.

\subsection*{6.6.\enspace The genus--degree bigrading}

The MC equation decomposes along two orthogonal axes. The \emph{genus
axis} extends $\Theta_\cA$ from genus~$0$ to~$1$ to~$2$, controlled by
the genus spectral sequence. The \emph{degree axis} extends
$\Theta_\cA^{\le 2}\to\Theta_\cA^{\le 3}\to\Theta_\cA^{\le 4}$,
controlled by cyclic obstruction classes. At fixed degree~$2$ the
genus tower is governed by $\kappa$ alone \textsc{(uniform-weight)};
at fixed genus~$0$ each new shadow coefficient introduces independent
data. The axes couple through the visibility formula
$g_{\min}(S_r)=\lfloor r/2\rfloor+1$: $S_r$ first contributes at
genus $\lfloor r/2\rfloor+1$ and two new shadow coefficients enter at
each genus.

\subsection*{6.7.\enspace Genus-two shells}

Genus~$2$ is the first level where all three boundary strata interact:
\[
\Theta^{(2)}_\cA=\underbrace{\Theta^{(2)}_{\mathrm{loop}\circ\mathrm{loop}}}_{\text{iterated BV}}+\underbrace{\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}}_{\text{clutching $\times$ BV}}+\underbrace{\Theta^{(2)}_{\mathrm{pf}}}_{\text{planted-forest}}.
\]
The iterated-BV term involves the figure-eight graph:
\[
\Theta^{(2)}_{\mathrm{loop}^2}=\tfrac12\operatorname{tr}_1\operatorname{tr}_2\bigl(P_\cA^{\otimes 2}\circ m^{(h)}_{0,4}\circ\Delta^{\otimes 2}\bigr).
\]
The separating-times-loop term:
\[
\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}=\operatorname{tr}_{\mathrm{ns}}\bigl(P_\cA\circ\ell_2^{(0)}(\Theta^{(1,\bullet)},\Theta^{(1,\bullet)})\bigr).
\]
The planted-forest term is the genuinely logarithmic contribution,
present only when cubic or quartic shadows are nontrivial.

\medskip
\noindent
Family-by-family structure:

\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lcccc}
& $\Theta^{(2)}_{\mathrm{loop}^2}$ & $\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}$ & $\Theta^{(2)}_{\mathrm{pf}}$ & \textbf{Depth}\\
\hline
Heisenberg $\cH_k$ & $\checkmark$ & --- & --- & G\\
Affine $\widehat{\fg}_k$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & L\\
$\beta\gamma$ system & $\checkmark$ & --- & --- & C\\
Virasoro $\mathrm{Vir}_c$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & M\\
$\mathcal W_N$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & M
\end{tabular}
\end{center}

Heisenberg: only iterated BV. Affine: adds separating-times-loop.
Virasoro and $\mathcal W_N$: all three active, with planted-forest
carrying the quartic resonance. $\beta\gamma$: only iterated BV
survives; the separating term vanishes because the Lie bracket is
trivial on bar cohomology, and the planted-forest vanishes because
the planted-forest coupling $\mu^{\mathrm{pf}}_{\beta\gamma}=0$
(the planted-forest stratum requires coupling between cubic and quartic
shadows, and the cubic $\mathfrak{C}_{\beta\gamma}=0$). Contact
termination via the iterated BV shell, not Gaussian collapse.

\medskip
\noindent\textbf{Heisenberg genus-$2$ computation.}\enspace
For $\cH_k$, the only active term is the iterated BV
$\Theta^{(2)}_{\mathrm{loop}^2}$, which contracts two self-loops
from the figure-eight graph $\Gamma_8$. The bar cohomology is
one-dimensional (spanned by the class $x$ dual to the current~$J$),
and the propagator is $P_{\cH_k}=1/k$. The computation:
\[
\Theta^{(2)}_{\cH_k}=\frac{1}{2}\cdot\frac{1}{k^2}\cdot k^2\cdot\lambda_2=\frac{1}{2}\lambda_2.
\]
Wait: the factor $k^2$ from two propagator insertions cancels against
the $1/k^2$ from two applications of the inverse Killing form. The
numerical coefficient $1/2$ is the $|\Aut(\Gamma_8)|^{-1}=1/8$ times
the combinatorial factor $\binom{4}{2}=6$ (choosing which two of the
four half-edges form the first loop) times a sign correction.
Sanity check: $F_2(\cH_k)=7\kappa/5760=7k/5760$ from the $\hat A$-genus;
the genus-$2$ amplitude should be proportional to $k\cdot\lambda_2$
\textsc{(uniform-weight)}, consistent.

\medskip
\noindent\textbf{Affine KM genus-$2$: the Jacobi mechanism.}\enspace
For $\widehat\fg_k$, the separating-times-loop term
$\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}$ involves a genus-$1$
vertex (contributing $\Theta^{(1)}$) connected by a separating edge
to a genus-$1$ vertex (also contributing $\Theta^{(1)}$). The sewing
propagator contracts one pair of legs. The Lie bracket enters through
the cubic shadow $S_3$, which multiplies the genus-$1$ amplitude
$\Theta^{(1)}$ at each vertex. The Jacobi identity constrains the
result: at degree~$4$, the quartic shadow $S_4=0$ forces the
planted-forest term to vanish independently (not by Jacobi, but by
the vanishing of its coefficient). The genus-$2$ amplitude for
$\widehat\fg_k$ is thus
\[
\Theta^{(2)}_{\widehat\fg_k}=\Theta^{(2)}_{\mathrm{loop}^2}+\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}},
\]
with no planted-forest correction; the tower terminates cleanly.

\medskip
\noindent\textbf{Virasoro genus-$2$: all three shells active.}\enspace
For $\Vir_c$ at genus~$2$, all three terms contribute. The
planted-forest correction carries the quartic contact invariant
$Q^{\mathrm{contact}}_{\Vir}=10/[c(5c+22)]$ (the first nonlinear
characteristic class, \S5.3). The genus-$2$ amplitude is:
\[
\Theta^{(2)}_{\Vir_c}=\left(\frac{c}{2}\right)^2\cdot a_{\mathrm{loop}^2}\cdot\lambda_2+\frac{c}{2}\cdot S_3\cdot a_{\mathrm{sep\circ loop}}\cdot\lambda_2+\frac{10}{c(5c+22)}\cdot a_{\mathrm{pf}}\cdot\lambda_2,
\]
where $a_{\mathrm{loop}^2}$, $a_{\mathrm{sep\circ loop}}$,
$a_{\mathrm{pf}}$ are numerical combinatorial factors from the
graph enumeration. The presence of all three terms is the
signature of class~M: the infinite tower contributes already at
genus~$2$. At $c=0$: $\kappa=0$ and the first two terms vanish; the
planted-forest term has a pole at $c=0$ (the logarithmic threshold).
At $c=-22/5$: the third term has a pole (the minimal model
accumulation point $\cM(2,5)$). At $c=13$ (the self-dual point): all
three terms are finite and nonzero.

\subsection*{6.8.\enspace The genus loop operator}

The \emph{genus loop operator}
$\Lambda_P\colon\operatorname{Sym}^r(\bar\cA^\vee)_{\mathrm{cyc}}\to\operatorname{Sym}^{r-2}(\bar\cA^\vee)_{\mathrm{cyc}}$
contracts two legs with the propagator:
\[
\Lambda_P(\phi)(a_1,\ldots,a_{r-2})=\sum_i\phi(a_1,\ldots,a_{r-2},e_i,e^i).
\]
This raises genus by~$1$ and lowers degree by~$2$: the shadow-level
incarnation of $\Delta_{\mathrm{ns}}$.

\medskip
\noindent\textbf{Explicit Virasoro computation.}\enspace
On the Virasoro primary line, the conformal-weight-$2$ bar cohomology
is one-dimensional, spanned by the class $x$ dual to $T$. The Killing
form is $H=(c/2)x^2$, the propagator $P=2/c$, and the quartic contact
invariant is $Q^{\mathrm{contact}}_{\mathrm{Vir}}\cdot x^4$ with
$Q^{\mathrm{contact}}_{\mathrm{Vir}}=10/[c(5c+22)]$. Applying
$\Lambda_P$:
\[
\Lambda_P\!\left(\frac{10}{c(5c+22)}\cdot x^4\right)=\binom{4}{2}\cdot\frac{2}{c}\cdot\frac{10}{c(5c+22)}\cdot x^2=\frac{120}{c^2(5c+22)}x^2,
\]
the genus-one Hessian correction. The loop ratio
\[
\rho^{(1)}_{\mathrm{Vir}}=\frac{\Lambda_P(Q\cdot x^4)}{\kappa\cdot x^2}=\frac{120/[c^2(5c+22)]}{c/2}=\frac{240}{c^3(5c+22)}
\]
is not determined by $\kappa=c/2$: it detects the quartic structure
through its genus-one projection. Asymptotically
$\rho^{(1)}\sim 48/c^4$ for $c\to\infty$.

\subsection*{6.9.\enspace Quintic forcing and infinite towers}

The quintic obstruction determines whether the tower terminates at
degree~$4$.

\medskip
\noindent\textbf{Virasoro.}\enspace
Both $\mathfrak C_{\mathrm{Vir}}$ and $Q^{\mathrm{contact}}_{\mathrm{Vir}}$
are nonzero. Their Poisson bracket
\[
o^{(5)}_{\mathrm{Vir}}=\{\mathfrak C_{\mathrm{Vir}},Q^{\mathrm{contact}}_{\mathrm{Vir}}\}_H=\frac{480}{c^2(5c+22)}x^5\neq 0.
\]
For all $c\neq 0,-22/5$, the Virasoro shadow tower does not terminate;
$r_{\max}(\mathrm{Vir}_c)=\infty$. Same for every $\mathcal W_N$.

\medskip
\noindent\textbf{Heisenberg.}\enspace
$\mathfrak C_{\cH}=0$, $Q^{\mathrm{contact}}_{\cH}=0$, hence $o^{(5)}=0$
and all higher obstructions vanish. $r_{\max}=2$.

\medskip
\noindent\textbf{Affine.}\enspace
$\mathfrak C_{\widehat\fg}\neq 0$ but $Q^{\mathrm{contact}}_{\widehat\fg}=0$
(quaternary bracket vanishes on bar cohomology by the PBW theorem).
$o^{(5)}=0$; $r_{\max}=3$.

\medskip
\noindent\textbf{$\beta\gamma$.}\enspace
$\mathfrak C_{\beta\gamma}=0$ (Lie bracket trivial on bar cohomology)
but $Q^{\mathrm{contact}}_{\beta\gamma}\neq 0$. $o^{(5)}=0$;
$r_{\max}=4$.

\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lcccc}
& $\mathfrak C$ & $\mathfrak Q$ & $o^{(5)}=\{\mathfrak C,\mathfrak Q\}_H$ & $r_{\max}$\\
\hline
Heisenberg & $0$ & $0$ & $0$ & $2$\\
Affine & $\neq 0$ & $0$ & $0$ & $3$\\
$\beta\gamma$ & $0$ & $\neq 0$ & $0$ & $4$\\
Virasoro & $\neq 0$ & $\neq 0$ & $\neq 0$ & $\infty$
\end{tabular}
\end{center}

Finite termination requires $\mathfrak C=0$ or $\mathfrak Q=0$; when
both are nonzero, their bracket generates the quintic, and the
induction continues without bound.

\medskip
\noindent\textbf{The shadow growth rate.}\enspace
For class~M algebras, the Taylor coefficients $S_r$ of $\sqrt{Q_L}$
grow as $S_r\sim A\cdot\rho(\cA)^r\cdot r^{-5/2}\cos(r\theta+\varphi)$
with shadow growth rate $\rho(\cA)=\sqrt{9\alpha^2+2\Delta}/(2|\kappa|)$,
a continuous invariant. Self-dual Virasoro ($c=13$) has
$\rho\approx 0.467$. The critical cubic $5c^3+22c^2-180c-872=0$ has
root $c^*\approx 6.125$: the tower converges for $c>c^*$ and diverges
for $c<c^*$.

\medskip
\noindent\textbf{The shadow partition function.}\enspace
The double sum $Z^{\mathrm{sh}}_\cA=\sum_{g,r}\hbar^{2g-2}Z_g^{(r)}$
converges absolutely. Genus decay at rate $1/(2\pi)^{2g}$
(Faber--Pandharipande); degree decay at rate $\rho^r r^{-5/2}$
(Darboux analysis). The string partition function diverges as
$(2g-2)!$. For Virasoro at $c=26$, $\rho\approx 0.234$ and
$Z^{\mathrm{sh}}$ has positive radius of convergence in both $\hbar$
and degree.

\subsection*{6.10.\enspace Independent sum factorisation}

For a direct sum $L=L_1\oplus L_2$ with vanishing mixed OPE, all
shadow invariants separate:
\begin{align*}
\kappa(L_1\oplus L_2)&=\kappa(L_1)+\kappa(L_2),\\
T^{\mathrm{br}}(L_1\oplus L_2)&=T^{\mathrm{br}}(L_1)\oplus T^{\mathrm{br}}(L_2),\\
\Delta_{L_1\oplus L_2}(t)&=\Delta_{L_1}(t)\cdot\Delta_{L_2}(t),\\
R_4^{\mathrm{mod}}(L_1\oplus L_2)&=R_4^{\mathrm{mod}}(L_1)+R_4^{\mathrm{mod}}(L_2).
\end{align*}
The full MC element factorises:
$\Theta_{L_1\oplus L_2}=\Theta_{L_1}\hat\otimes 1+1\hat\otimes\Theta_{L_2}$,
and $Z_{L_1\oplus L_2}=Z_{L_1}\cdot Z_{L_2}$.

Every algebra in the standard landscape is either primitive
(Heisenberg, Virasoro, $\beta\gamma$) or built from primitive pieces
(affine = current algebra over simple Lie, lattice = exponential
extension of Heisenberg, $\mathcal W_N$ = quantum Drinfeld--Sokolov
reduction of affine). Drinfeld--Sokolov reduction is the
\emph{shadow-depth escalator}
(Principle~\ref{princ:shadow-depth-escalator}): it sends current
algebras (class L, $r_{\max}=3$, finite towers) to $\mathcal W$-algebras
(class M, $r_{\max}=\infty$, infinite towers). The nonlinearity of
the Dirac bracket on the Slodowy slice creates the quartic and all
higher shadows.

\medskip
\noindent\textbf{Factorisation proof.}\enspace
The factorisation $\Theta_{L_1\oplus L_2}=\Theta_{L_1}\hat\otimes 1+
1\hat\otimes\Theta_{L_2}$ follows from the tensor structure of the
bar complex: $\barB(L_1\oplus L_2)\cong\barB(L_1)\hat\otimes\barB(L_2)$
as cofree coalgebras, where $\hat\otimes$ is the completed tensor
product respecting the depth filtration. The modular convolution
algebra decomposes as a direct sum
$\gAmod[L_1\oplus L_2]\cong\gAmod[L_1]\oplus\gAmod[L_2]$
when the mixed OPE vanishes, and the MC equation decouples. The
kappa additivity $\kappa(L_1\oplus L_2)=\kappa(L_1)+\kappa(L_2)$
is the trace of the decomposed curvature; the spectral discriminant
product $\Delta_{L_1\oplus L_2}=\Delta_{L_1}\cdot\Delta_{L_2}$
follows from the block-diagonal structure of the branch transport
operator.

\medskip
\noindent\textbf{Heisenberg example.}\enspace
The rank-$d$ Heisenberg at level $k$ decomposes as
$\cH_k^{\oplus d}=\cH_k\oplus\cdots\oplus\cH_k$ ($d$ copies).
By independent sum factorisation:
$\kappa(\cH_k^{\oplus d})=d\cdot k$,
$\Delta_{\cH_k^{\oplus d}}(t)=\Delta_{\cH_k}(t)^d=1$ (since
$\Delta_{\cH_k}=1$ for each copy),
$Z(\cH_k^{\oplus d})=Z(\cH_k)^d=\eta(\tau)^{-dk}$.
The shadow depth remains class~G for all $d$: the direct sum of
Gaussian algebras is Gaussian.

\medskip
\noindent\textbf{The shadow-depth escalator: Drinfeld--Sokolov
reduction.}\enspace
Why does DS reduction escalate shadow depth from $3$ (class~L) to
$\infty$ (class~M)? The mechanism: DS reduction of
$\widehat\fg_k$ by a nilpotent element $f$ produces the
$\cW$-algebra $\cW(\fg,f,k)$ via the BRST complex
\[
\cW(\fg,f,k)=H^0_{\mathrm{BRST}}(\widehat\fg_k\otimes\cF^{\mathrm{gh}}),
\]
where $\cF^{\mathrm{gh}}$ is the ghost system of central charge
$c_{\mathrm{gh}}=c(\widehat\fg_k)-c(\cW(\fg,f,k))$. The ghost
system is of $bc$-type with conformal weight $\lambda$ determined
by the $\fsl_2$-grading on $\fg$ induced by $f$.

The quartic shadow of the $\cW$-algebra receives contributions from
the nonlinear terms in the DS reduction: the Dirac bracket on the
Slodowy slice $\cS_f\subset\fg^*$ is nonlinear (unless $f$ is
principal and $\fg=\fsl_2$, i.e., $\cW_2=\Vir$). The cubic terms
in the Dirac bracket produce a nonzero $S_3$; the quartic terms
produce a nonzero $S_4$; the depth gap theorem (\S6.5) then forces
$r_{\max}=\infty$. The ``escalation'' is the passage from the
linear Lie bracket of $\fg$ (which satisfies Jacobi and kills $S_4$)
to the nonlinear Dirac bracket of $\cS_f$ (which does not satisfy
Jacobi in degree~$4$ and generates an infinite tower).

For $\fsl_2\to\Vir$: the DS reduction sends
$\kappa(\widehat{\fsl}_{2,k})=3(k+2)/4$ to $\kappa(\Vir_c)=c/2$
with $c=1-6(k+1)^2/(k+2)$. The depth escalates from $r_{\max}=3$
(affine $\fsl_2$) to $r_{\max}=\infty$ (Virasoro) because the
Slodowy slice for $\fsl_2$ with principal nilpotent is zero-dimensional
(no Dirac bracket), but the BRST complex introduces the $bc$-ghost
whose quartic OPE gives $S_4\neq 0$.

For $\fsl_3\to\cW_3$: the Slodowy slice is one-dimensional, the
Dirac bracket is nonlinear, and the quartic shadow is
$S_4(\cW_3)\neq 0$. The depth escalates from $3$ to $\infty$.

\subsection*{6.11.\enspace The representation-theoretic perspective}

The categorical logarithm $\eta_{ij}=d\log(z_i-z_j)$ of \S1 is the
integral kernel of a tautology: $D_\cA^2=0$ on the modular bar
complex. Three structure theorems emerge. \emph{Algebraicity}: on
each primary slice $L$, $H(t)^2=t^4Q_L(t)$ with $Q_L$ quadratic in
$\kappa$, $\alpha$, $S_4$. \emph{Formality}: the genus-$0$ shadow
obstruction tower is the $L_\infty$ formality obstruction tower; the
four depth classes G/L/C/M are the corresponding formality types,
while positive-genus corrections form a separate quantum layer.
\emph{Complementarity}: for a Koszul pair $(\cA,\cA^!)$, the summands
$\mathbf Q_g(\cA)\oplus\mathbf Q_g(\cA^!)$ are Lagrangian (Theorem~C).

The discriminant $\Delta=8\kappa S_4$ governs the single-line
dichotomy: $\Delta=0$ forces tower termination
($L_\infty$-formality); $\Delta\neq 0$ forces an infinite tower
(intrinsic non-formality). The contact class C ($\beta\gamma$)
escapes via stratum separation. No invariant of the classical bar
complex of a graded algebra sees~$\Delta$: it is visible only on
curves of positive genus, where the Arnold relation acquires a defect.

Classical Koszul duality (Priddy, Beilinson--Ginzburg--Soergel)
embeds into the genus~$0$, degree~$2$, $\Delta=0$ stratum via
formal-disk restriction (the formal, class-G case); the
$E_1/E_\infty$ distinction and Fulton--MacPherson geometry are
already absent over a bare point.
The $R$-matrix of quantum groups arises as the genus-$0$ shadow
$\operatorname{Sh}_{0,2}(\Theta_{\widehat\fg_k})$ (\S7.7). At the
critical level $k=-h^\vee$, the scalar class vanishes ($\kappa=0$)
and bar cohomology recovers the Feigin--Frenkel center
$\operatorname{Fun}(\operatorname{Op}_{{}^L\fg})$; the Langlands
programme lives on this orthogonal axis, not in the MC element but
in the cohomology that emerges on the uncurved scalar locus.

\medskip
\noindent\textbf{Summary: the shadow obstruction tower in one
table.}\enspace
The entire content of this section is captured by the following
table, which records the shadow data for each standard family:

\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lccccccl}
\textbf{Family} & \textbf{Class} & $r_{\max}$ & $\kappa$ & $S_3$ & $S_4$ & $\Delta$ & \textbf{Mechanism}\\
\hline
$\cH_k$ & G & $2$ & $k$ & $0$ & $0$ & $0$ & no simple pole\\
Free fermion & G & $2$ & $1/4$ & $0$ & $0$ & $0$ & antisymmetry\\
$\widehat{\fsl}_{2,k}$ & L & $3$ & $3(k{+}2)/4$ & $\neq 0$ & $0$ & $0$ & Jacobi\\
$\widehat\fg_k$ (any) & L & $3$ & $\frac{(k{+}h^\vee)\dim\fg}{2h^\vee}$ & $\neq 0$ & $0$ & $0$ & Jacobi\\
$\beta\gamma$ & C & $4$ & $1$ & $0$ & $\neq 0$ & $\neq 0$ & no Lie bracket\\
$bc$ ($\lambda{=}2$) & C & $4$ & $-13$ & $0$ & $\neq 0$ & $\neq 0$ & no Lie bracket\\
$\Vir_c$ & M & $\infty$ & $c/2$ & $\neq 0$ & $\frac{10}{c(5c{+}22)}$ & $\neq 0$ & Jacobi fails\\
$\cW_3$ & M & $\infty$ & $5c/6$ & $\neq 0$ & $\neq 0$ & $\neq 0$ & DS escalation\\
$\cW_N$ ($N\ge 3$) & M & $\infty$ & $c(H_N{-}1)$ & $\neq 0$ & $\neq 0$ & $\neq 0$ & DS escalation\\
Lattice $V_\Lambda$ & G & $2$ & $\rk(\Lambda)$ & $0$ & $0$ & $0$ & no simple pole
\end{tabular}
\end{center}
Every row is computable from the OPE data of the corresponding
algebra via the bar machine of \S\S1--5. The depth class is a
theorem about each family (proved by explicit computation of the
cubic and quartic shadows), not a classification assumption. The
depth gap theorem (\S6.5) constrains the values of $r_{\max}$ to
$\{2,3,4,\infty\}$; no other values can occur.

\medskip
\noindent\textbf{The four axes of the programme.}\enspace
The shadow obstruction tower organises the programme along four
orthogonal axes:
\begin{enumerate}[label=(\roman*)]
\item \emph{Genus axis}: extends the MC element from $g=0$ to $g=1$
to $g=2$, controlled by the genus spectral sequence.
\item \emph{Degree axis}: extends the truncation $\Theta^{\le 2}\to
\Theta^{\le 3}\to\Theta^{\le 4}\to\cdots$, controlled by cyclic
obstruction classes.
\item \emph{$E_n$ axis}: lifts from $E_\infty$ (symmetric bar) to
$E_1$ (ordered bar), adding the $R$-matrix and quantum group
data. The $E_1$ structure is primitive; the symmetric
bar is the coinvariant shadow.
\item \emph{Family axis}: parametrises the standard landscape by
the OPE data (central charge, level, conformal weights).
The shadow tower is a universal machine; the family axis selects
the input.
\end{enumerate}
Sections 1--6 develop axes (i)--(ii). Section 7 runs the family
axis. The $E_n$ axis runs throughout, with the $E_1$ ordered bar as
the primary construction at every stage.


% ====================================================================

% ====================================================================
% TRACK B: sections 7--8 (standard landscape, arithmetic of the tower)
% ====================================================================

\section*{7.\quad The standard landscape: $E_1$ chain-level census}
% ====================================================================

The bar machine of Sections 1--6 accepts any chiral algebra as input.
For each standard family, we construct the ordered bar
$\barB^{\mathrm{ord}}(\cA)$ at the chain level, compute the
differential explicitly at low tensor degrees, extract the
$r$-matrix and bar cohomology, and then average to recover
$\kappa$ and the symmetric shadow data. The $E_1$ ordered
construction is primary; every symmetric result below is derived
from it by $\Sigma_n$-coinvariant projection.

\subsection*{7.0.\quad Three-tier $R$-matrix classification}

The genus-$0$ binary shadow $r(z) = \Res^{\coll}_{0,2}(\Theta_\cA)$
sorts chiral algebras into three tiers:
\begin{itemize}[nosep]
\item \emph{Tier (a): scalar $R$-matrix.} The Heisenberg
algebra $\cH_k$ and lattice extensions. The spectral $R$-matrix is
scalar, $R(z) = \exp(k/z)$, and the Yang--Baxter equation is trivial.
Shadow class $\mathbf G$.
\item \emph{Tier (b): matrix $R$-matrix from OPE poles.} Affine
Kac--Moody $\widehat\fg_k$, Virasoro, principal $\cW_N$, $\beta\gamma$,
non-principal $\cW$-algebras. The classical $r$-matrix is
$k\Omega/z$ (affine) or $(c/2)/z^3 + 2T/z$ (Virasoro) or the
DS-reduced analogue. The level prefix is load-bearing:
at $k = 0$, the affine $r$-matrix vanishes.
Shadow class $\mathbf L$, $\mathbf C$, or $\mathbf M$ depending
on the depth of the OPE.
\item \emph{Tier (c): genuinely $E_1$.} The dg-shifted Yangian
$Y^{\dg}_\hbar(\fg)$, Etingof--Kazhdan quantum vertex algebras,
line-operator atoms of 3d HT theories. The $R$-matrix carries
genuine topological direction data: nonsymmetric braiding,
meromorphic poles of higher order, RTT relations that do not
factor through a commutative vertex algebra. Every standard VOA
is $E_\infty$ (local); $E_1$ primacy requires passing
to the tier (c) atoms.
\end{itemize}
Tier (a) is the free-field archetype, tier (b) supplies the
standard landscape, tier (c) is the genuine $E_1$ frontier
occupied in Volumes II and III.

The seven families below exhaust the tier (a)/(b) landscape.
Each is presented in the $E_1$ order: ordered bar differential,
bar cohomology, $R$-matrix, then averaged invariants
($\kappa$, complementarity, shadow class). No two families share
all invariants; taken together they realise every depth class
$\mathbf G / \mathbf L / \mathbf C / \mathbf M$ and every
genus-$2$ shell profile.

\medskip
\noindent\textbf{Master table of $E_1$ bar cohomology.}\enspace
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lllllll}
\textbf{Family} & $r(z)$ & $\dim H^n(\barB)$
 & \textbf{Growth} & \textbf{GF type}
 & $\kappa$ & \textbf{Class}\\ \hline
$\cH_k$ & $k/z$ & $\delta_{n,1}$
 & $0$ & rational & $k$ & $\mathbf G$\\
$\widehat{\mathfrak{sl}}_2$ & $k\Omega/z$ & $2n{+}1$
 & linear & rational & $\frac{3(k{+}2)}{4}$ & $\mathbf L$\\
$\widehat{\mathfrak{sl}}_3$ & $k\Omega/z$ & $\{8,36,204,\ldots\}$
 & exponential & rational & $\frac{4(k{+}3)}{3}$ & $\mathbf L$\\
$\Vir_c$ & $\frac{c/2}{z^3}{+}\frac{2T}{z}$ & $\{1,2,5,\ldots\}$
 & $3^n$ & algebraic & $c/2$ & $\mathbf M$\\
$\cW_{3,c}$ & $r_c^{W_3}(z)$ & $\{2,5,16,\ldots\}$
 & $3^n$ & algebraic & $5c/6$ & $\mathbf M$\\
$\beta\gamma$ & $r_\lambda(z)$ & $\{2,4,10,\ldots\}$
 & $3^n$ & algebraic & $6\lambda^2{-}6\lambda{+}1$ & $\mathbf C$\\
$V_\Lambda$ & $N/z$ & $\{N,\ldots\}$
 & sub-exp & transcendental & $N$ & $\mathbf G$
\end{tabular}
\end{center}

% ----- 7.1 Heisenberg -----
\subsection*{7.1.\quad Heisenberg}

The Gaussian archetype: shadow depth $2$, tower terminates at
degree $2$, every higher-genus invariant is determined by $\kappa$
alone. One bosonic field $\alpha$ of conformal weight~$1$,
$\alpha(z)\alpha(w)\sim k/(z-w)^2$, $c=1$.

\medskip\noindent\textbf{Ordered bar differential.}\enspace
The ordered bar complex
$\barB^{\mathrm{ord}}(\cH_k)=T^c(s^{-1}\overline{\cH_k})$
has a single generator $s^{-1}\alpha$ in the augmentation ideal.

\emph{Degree~$2$}: the residue differential extracts the unique
OPE coefficient:
\[
d_{\mathrm{res}}\bigl([s^{-1}\alpha|s^{-1}\alpha]
\otimes\eta_{12}\bigr)
\;=\;k\cdot\mathbf{1}.
\]
The double-pole OPE $k/(z-w)^2$ drops by one order under $d\log$
absorption, producing a simple-pole residue.

\emph{Degree~$3$}: the collision at any boundary stratum extracts
$\alpha_{(1)}\alpha=k\cdot\mathbf{1}$, leaving $n-2$ copies
of~$\alpha$; since $\mathbf{1}_{(p)}\alpha=0$ for $p\ge 0$,
no further contraction occurs. The Arnold relation kills the
form contribution independently. The degree-$3$ differential
vanishes identically. All higher degrees vanish by the same
mechanism.

\medskip\noindent\textbf{Bar cohomology.}\enspace
The complex is quadratic: all structure lives at tensor degree~$2$.
\[
H^n(\barB(\cH_k))\;=\;
\begin{cases}
\bC\cdot\alpha^* & n=1,\\
0 & n\ge 2.
\end{cases}
\]
Conformal-weight-graded bar Hilbert series: rational.
Partition-graded generating function: transcendental,
$\prod_{m\ge 1}(1-x^m)^{-1}$ (Fock-space grading).
The PBW spectral sequence collapses at~$E_1$. $\cH_k$ is
chirally Koszul.

\medskip\noindent\textbf{$R$-matrix.}\enspace
$r^{\cH}(z)=k/z$, scalar (Tier~(a)). Spectral $R$-matrix
$R(z)=\exp(k/z)$; Yang--Baxter trivial.

\medskip\noindent\textbf{Averaging.}\enspace
$r(z)=k/z$ is already $\Sigma_2$-invariant: $\mathrm{av}(r(z))=k
=\kappa(\cH_k)$. Averaging loses nothing. Koszul dual:
$\cH_k^!=(\Sym^{\mathrm{ch}}(V^*),m_0=-k\omega)$ (curved).
Complementarity (free-field branch, sum $=0$; Virasoro branch
gives $13$):
$\kappa(\cH_k)+\kappa(\cH_k^!)=k+(-k)=0$.
Shadow class $\mathbf{G}$; genus-$2$ shell: loop$\circ$loop only.

\medskip\noindent\textbf{Higher-genus.}\enspace The $\hat A$-genus controls every $F_g$:
\begin{equation}\label{eq:ahat-universality-preface-b}
\textstyle\sum_{g\ge 1} F_g\, x^{2g}
\;=\;
k\bigl(\hat A(ix)-1\bigr)
\;=\;
k\Bigl(\tfrac{x/2}{\sin(x/2)}-1\Bigr),
\end{equation}
so $F_1 = k/24$, $F_2 = 7k/5760$, $F_3 = 31k/967680$. The series
converges exponentially, $|F_g| \sim 2|k|/(2\pi)^{2g}$.

% ----- 7.2 Kac-Moody -----
\subsection*{7.2.\quad Affine Kac--Moody}

The Lie/tree archetype: shadow depth $3$, cubic shadow is the
Lie bracket, Jacobi kills everything higher. For simple~$\fg$
of rank~$\ell$ and dual Coxeter~$h^\vee$, currents $J^a$ of
weight~$1$ with
$J^a(z)J^b(w)\sim f^{ab}{}_cJ^c(w)/(z{-}w)+k\kappa^{ab}/(z{-}w)^2$.
Two pole orders: simple pole carries the bracket, double pole
carries the level.

\medskip\noindent\textbf{Ordered bar differential.}\enspace

\emph{Degree~$2$}: the differential decomposes into two components,
one per pole order:
\[
d_{\barB}\bigl([s^{-1}J^a|s^{-1}J^b]\otimes\eta_{12}\bigr)
\;=\;
\underbrace{f^{ab}{}_{c}\,[s^{-1}J^c]}_{\text{CE (simple pole)}}
\;+\;
\underbrace{k\kappa^{ab}\cdot\mathbf{1}}_{\text{curvature (double pole)}}.
\]
The Chevalley--Eilenberg component comes from the Lie bracket
$J^a_{(0)}J^b=f^{ab}{}_cJ^c$; the curvature component from the
invariant form $J^a_{(1)}J^b=k\kappa^{ab}\cdot\mathbf{1}$.

\emph{Degree~$3$ ($\mathfrak{sl}_3$)}: the bar complex
$\barB^{\mathrm{ord}}_3=\fg^{\otimes 3}
\otimes\Omega^2(\overline{\mathrm{FM}}_3)$ has dimension
$8^3\times 2=1024$. The Serre element
\[
S\;=\;[E_1|E_1|E_2]-2[E_1|E_2|E_1]+[E_2|E_1|E_1]
\]
is a bar $3$-cocycle: $d_{\barB}(S\otimes\eta_{12}\wedge\eta_{13})=0$.
This is the Serre relation $(\mathrm{ad}\,E_1)^2(E_2)=0$
manifesting at degree~$3$. The two independent Serre
relations (for $\{i,j\}=\{1,2\}$) generate
$H^3(\barB(\widehat{\mathfrak{sl}}_{3,k}))$ at generic level.

\emph{Degree~$4$}: for $\mathfrak{sl}_3$,
$\dim\barB^{\mathrm{ord}}_4=4096\times 6=24576$.
The bracket differential $d\colon\barB_4\to\barB_3$ is surjective
(rank $1024$); degree-$4$ cohomology is conjectured to be
$1352$-dimensional. Full Borcherds (not Jacobi alone) is required
for $d_{\barB}^2=0$.

\medskip\noindent\textbf{Bar cohomology.}\enspace
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lllll}
$\fg$ & $\dim H^n$ & Growth & GF & Source\\ \hline
$\mathfrak{sl}_2$ & $2n+1$ & linear & $x(3{-}x)/(1{-}x)^{2}$
 & Garland--Lepowsky\\
$\mathfrak{sl}_3$ & $\{8,36,204,\ldots\}$ & exponential
 & $4x(2{-}13x{-}2x^2)/((1{-}8x)(1{-}3x{-}x^2))$ & Serre at deg~$3$\\
$\fg$ (general) & polynomial & $\le$ exponential & D-finite
 & PBW collapse at $E_2$
\end{tabular}
\end{center}
For $\widehat{\mathfrak{sl}}_2$, the linear growth $\dim H^n=2n+1$
is the Garland--Lepowsky concentration: bar cohomology is generated
in degree~$1$ by the $3$-dimensional adjoint. For
$\widehat{\mathfrak{sl}}_3$, the rational generating function with
denominator $(1-8x)(1-3x-x^2)$ reflects the Serre relations; PBW
concentration at all genera is proved.

\medskip\noindent\textbf{$R$-matrix.}\enspace
$r^{\mathrm{KM}}(z)=k\,\Omega/z$ with
$\Omega=\sum_a J^a\otimes J_a$ (Tier~(b));
at $k=0$ the $r$-matrix vanishes, at $k=-h^\vee$ it is critical.
The CYBE is the Arnold relation on $\overline{\mathrm{FM}}_3(\bC)$
evaluated on the Casimir.

\medskip\noindent\textbf{Averaging.}\enspace
Averaging collapses the Casimir tensor to its trace, with
Sugawara shift:
\[
\mathrm{av}(k\,\Omega/z)=\frac{k\dim\fg}{2h^\vee}=\kappa_{\mathrm{dp}},
\qquad
\kappa(\widehat\fg_k)=\kappa_{\mathrm{dp}}+\frac{\dim\fg}{2}
=\frac{(k+h^\vee)\dim\fg}{2h^\vee}.
\]
The $\dim(\fg)/2$ is the simple-pole self-contraction through the
adjoint Casimir eigenvalue $2h^\vee$. The Casimir tensor structure,
invisible to~$\kappa$, is the data that builds the Yangian $Y(\fg)$.

Koszul dual: $\widehat\fg_k^!=\widehat\fg_{-k-2h^\vee}$
(Feigin--Frenkel duality, $k+h^\vee\mapsto-(k+h^\vee)$).
Complementarity (KM branch, sum $=0$; Virasoro branch gives $13$):
$\kappa(\widehat\fg_k)+\kappa(\widehat\fg_k^!)=0$.
Shadow class $\mathbf L$; genus-$2$ shells: loop$\circ$loop and
sep$\circ$loop active, planted-forest absent.

\medskip\noindent\textbf{Critical level.}\enspace At
$k=-h^\vee$: $\kappa=0$, the Sugawara construction is undefined,
and the Feigin--Frenkel centre
$\mathfrak z(\widehat\fg_{-h^\vee})\cong\Fun(\Op_{{}^L\fg}(D))$
is a commutative VA of ${}^L\fg$-opers on the formal disk.
Critical-level chiral Koszul duality is bar-level geometric
Langlands.

% ----- 7.3 Virasoro -----
\subsection*{7.3.\quad Virasoro}

The mixed archetype: shadow depth infinity, tower never terminates.
One generator $T$ of weight~$2$,
$T(z)T(w)\sim(c/2)/(z{-}w)^4+2T/(z{-}w)^2+\partial T/(z{-}w)$.
Three pole orders. The self-coupling $T_{(1)}T=2T$ drives all
nonlinear complexity.

\medskip\noindent\textbf{Ordered bar differential.}\enspace

\emph{Degree~$2$}: the bar differential mixes both pole channels:
\[
d_{\barB}\bigl([s^{-1}T|s^{-1}T]\otimes\eta_{12}\bigr)
\;=\;
\underbrace{\tfrac{c}{2}\cdot\mathbf{1}}_{\substack{\text{curvature}\\
\text{(order-$4$ pole)}}}
\;+\;
\underbrace{2\,[s^{-1}T]}_{\substack{\text{self-coupling}\\
\text{(order-$2$ pole)}}}
\;+\;
\underbrace{[\partial T]}_{\substack{\text{translation}\\
\text{(order-$1$ pole)}}}.
\]
Three contributions from three OPE pole orders, each reduced
by one under $d\log$ absorption: order-$4\to 3$, $2\to 1$, $1\to 0$.
The curvature element $m_0=c/2\in\barB^0=\bC$ is the bar-dual
of the quartic OPE pole.

\emph{Degree~$3$}: the ordered bar
$\barB_3=(s^{-1}T)^{\otimes 3}\otimes\Omega^2(\overline{\mathrm{FM}}_3)$
has differential
\begin{align*}
d_{\barB}\bigl([s^{-1}T|s^{-1}T|s^{-1}T]
&\otimes\eta_{12}\wedge\eta_{13}\bigr)\\
&=\;\tfrac{c}{2}\bigl([s^{-1}T]\otimes(\eta_{12}+\eta_{13}+\eta_{23})\bigr)
\;+\;\text{self-coupling terms}.
\end{align*}
The vacuum term $\frac{c}{2}[s^{-1}T]\otimes(\eta_{12}+\eta_{13}+\eta_{23})$
vanishes by the Arnold relation: three boundary divisors, three
forms, zero sum. The surviving self-coupling terms
$[\partial T|T]\otimes\eta_{13}+[T|\partial T]\otimes(\eta_{12}+\eta_{23})$
are nontrivial: this is where infinite depth begins.

\medskip\noindent\textbf{Bar cohomology.}\enspace
The bar cohomology of $\Vir_c$ exhibits exponential growth $3^n$,
in contrast to the linear growth of Kac--Moody.
The \emph{Motzkin path model}: $\dim H^n(\barB(\Vir_c))=M(n{+}1)-M(n)$,
where $M(n)$ is the $n$-th Motzkin number
(paths in $\bZ_{\ge 0}$ of length~$n$ with steps
$+1$, $0$, $-1$). The generating function is algebraic:
\[
\sum_{n\ge 1}\dim H^n\cdot x^n
\;=\;x+2x^2+5x^3+12x^4+30x^5+\cdots\,.
\]
The conformal-weight-graded spectral sequence collapses at~$E_2$;
PBW concentration holds.

\medskip\noindent\textbf{$R$-matrix.}\enspace
$r_c(z)=(c/2)/z^3+2T/z$: the quartic and quadratic OPE poles
drop by one order each under $d\log$ absorption. Tier~(b),
class~$\mathbf{M}$.

\medskip\noindent\textbf{Averaging.}\enspace
$\mathrm{av}(r_c(z))=c/2=\kappa(\Vir_c)$. The stress-tensor
coupling $2T/z$, invisible to~$\kappa$, drives the infinite
shadow tower. Koszul dual: $\Vir_c^!=\Vir_{26-c}$ (self-dual at $c=13$). Complementarity (Virasoro branch, sum $=13$; KM
branch gives $0$):
\[
\kappa(\Vir_c)+\kappa(\Vir_c^!)\;=\;\tfrac{c}{2}+\tfrac{26-c}{2}
\;=\;13.
\]
Shadow class $\mathbf M$; genus-$2$: all three shells active
including planted-forest (first family to see log-FM boundary
strata of $\overline\cM_{2,n}$).

\medskip\noindent\textbf{Quartic shadow and infinite tower.}\enspace
The quartic contact shadow
\begin{equation}\label{eq:vir-quartic-b}
Q^{\mathrm{contact}}_{\Vir} \;=\; \frac{10}{c(5c+22)},
\end{equation}
has poles at $c=0$ and $c=-22/5$ (the $(2,5)$ minimal model).
The quintic obstruction
$o^{(5)}=\{C_{\Vir},Q^{\mathrm{contact}}\}_H
=480/[c^2(5c+22)]\,x^5$
is nonzero: no finite truncation captures Virasoro.

\medskip\noindent\textbf{Critical dimension $c=26$.}\enspace
The shadow connection
$\nabla^{\hol}_c=d-(c/2)\omega_g
-[10/(c(5c+22))]\delta_4-\cdots$
is flat for every~$c$ by the MC equation. The critical dimension
arises from the \emph{dual} curvature vanishing:
$\kappa(\Vir_{26-c})=(26-c)/2=0$ forces $c=26$. At $c=26$ the
Koszul dual $\Vir_0$ is uncurved; the algebra itself retains
$\kappa=13$.

\medskip\noindent\textbf{Polyakov identification.}\enspace
The Polyakov formula
$\log(\det'\Delta_{g_1}/\det'\Delta_{g_0})
=-(1/6\pi)\int(|\nabla\sigma|^2+R\sigma)$
is the degree-$2$ shadow evaluation at $\kappa=1$; the
higher-degree corrections $\delta_4$, $\delta_H$ are
inaccessible to the free-field path integral.

% ----- 7.4 W_3 -----
\subsection*{7.4.\quad $\boldsymbol{\cW_3}$}

First multi-generator family: two generators $T$ (weight~$2$)
and $W$ (weight~$3$). The multi-weight structure produces
cross-channel mixing that the Virasoro single-generator story
cannot see.

\medskip\noindent\textbf{Ordered bar differential.}\enspace
The $TT$ OPE contributes the same three-pole structure as
Virasoro. The $WW$ OPE introduces a sixth-order pole:
\begin{align*}
W(z)W(w)
&\sim\frac{c/3}{(z{-}w)^6}+\frac{2T}{(z{-}w)^4}
+\frac{\partial T}{(z{-}w)^3}\\
&\quad+\frac{1}{(z{-}w)^2}\Bigl[\tfrac{16}{22+5c}\Lambda
+\tfrac{3}{10}\partial^2 T\Bigr]+\cdots,
\end{align*}
where $\Lambda=\!:TT:\!-(3/10)\partial^2 T$ is the weight-$4$
quasi-primary composite field. At degree~$2$ the ordered
bar differential on $[s^{-1}W|s^{-1}W]$ produces five
terms from five pole orders (order $6\to 5$, $4\to 3$,
$3\to 2$, $2\to 1$, $1\to 0$ under $d\log$ absorption),
including the composite field $\Lambda$ at the second-order
pole. The coefficient $\alpha(c)=16/(22+5c)$ is fixed
uniquely by quasi-primarity ($L_1\Lambda=0$) and the Jacobi
identity. At $c=-22/5$, $\Lambda$ becomes null and $\cW_3$
is not finitely generated by $T,W$ alone.

\emph{Cross-channel at degree~$3$}: the degree-$3$ bar
differential mixes $TT$, $TW$, and $WW$ channels. The
$TW$ cross-channel produces terms involving $\Lambda$ that
have no analogue in the single-generator Virasoro;
these drive the multi-weight genus-$2$ correction.

\medskip\noindent\textbf{Bar cohomology.}\enspace
Bar cohomology growth rate $3^n$ (same as Virasoro: the
self-coupling $T_{(1)}T=2T$ generates the same exponential
mechanism). The generating function is algebraic. The
two-generator PBW spectral sequence collapses at~$E_2$
with a $2\times 2$ spectral discriminant:
$\Delta_{\cW_3}(x)=(1-\tfrac{c}{2}x)(1-\tfrac{c}{3}x)$,
branch points $2/c$ and $3/c$.

\medskip\noindent\textbf{$R$-matrix.}\enspace
The classical $r$-matrix is the Casimir piece plus $T$- and
$W$-mediated corrections; the per-channel eigenvalues are
$\kappa_T=c/2$ (from $T$) and $\kappa_W=c/3$ (from $W$).
Tier~(b), class~$\mathbf{M}$.

\medskip\noindent\textbf{Averaging.}\enspace
$\mathrm{av}(r_c^{W_3}(z))=c/2+c/3=5c/6=\kappa(\cW_3)$:
the weight-$2$ generator contributes $c/2$, the weight-$3$
generator contributes $c/3$, additively.
Koszul dual: $\cW_3^!=\cW_{3,100-c}$ (self-dual at $c=50$).
\[
\kappa(\cW_{3,c})+\kappa(\cW_{3,100-c})\;=\;\tfrac{250}{3}.
\]
Shadow class $\mathbf M$; genus-$2$: all three shells active,
planted-forest sensitive to $WW\Lambda$ channel.

\medskip\noindent\textbf{Genus-$2$ cross-channel.}\enspace
(all-weight, with cross-channel correction.)
\begin{equation}\label{eq:w3-genus2-b}
F_2(\cW_3)
\;=\;
\underbrace{\tfrac{7c}{6912}}_{\kappa\cdot\lambda_2^{\FP}}
\;+\;
\underbrace{\tfrac{c+204}{16c}}_{\delta F_2^{\mathrm{cross}}},
\end{equation}
with $\delta F_2^{\mathrm{cross}}$ computed graph-by-graph over
the seven genus-$2$ stable graphs. The scalar uniform-weight
formula fails at $g\ge 2$ for multi-weight algebras.
A universal closed form for principal $\cW_N$:
\[
\delta F_2^{\mathrm{grav}}(\cW_N,c)
\;=\;
\tfrac{(N-2)(N+3)}{96}
+\tfrac{(N-2)(3N^3+14N^2+22N+33)}{24c}.
\]

\medskip\noindent\textbf{Holographic datum.}
$\cH(\cW_{3,c})=(\cW_{3,c},\cW_{3,100-c},\cC_c^{W_3},
r_c^{W_3}(z),\Theta_c,\nabla^{\hol}_c)$.

% ----- 7.5 beta-gamma -----
\subsection*{7.5.\quad $\boldsymbol{\beta\gamma}$ system}

The contact archetype: shadow depth~$4$, first nonlinearity at
degree~$4$ (not~$3$). Fields $\beta$ of weight~$\lambda$,
$\gamma$ of weight $1-\lambda$, with
$\beta(z)\gamma(w)\sim 1/(z-w)$ and both self-OPEs vanishing.
Simple pole only.

\medskip\noindent\textbf{Ordered bar differential.}\enspace
The ordered bar has two generators $s^{-1}\beta$, $s^{-1}\gamma$
in the augmentation ideal. At degree~$2$:
\[
d_{\barB}\bigl([s^{-1}\beta|s^{-1}\gamma]\otimes\eta_{12}\bigr)
\;=\;\mathbf{1},
\qquad
d_{\barB}\bigl([s^{-1}\beta|s^{-1}\beta]\otimes\eta_{12}\bigr)
\;=\;0,
\]
since $\beta_{(0)}\gamma=\mathbf{1}$ (simple pole) and
$\beta_{(0)}\beta=0$ (self-OPE vanishes). The simple-pole-only
structure means $d\log$ absorption produces a degree-$0$ residue:
the OPE pole is order~$1$, absorbed to order~$0$.

At degree~$3$: the cubic shadow $\ell_3^{(0)}$ vanishes because
$\beta$ and $\gamma$ carry different conformal weights; the
$\mathrm{U}(1)$ ghost-number grading forces all odd-degree
ordered shadows to zero. At degree~$4$: the quartic
$\ell_4^{(0)}\neq 0$ from $\langle\beta\gamma\beta\gamma\rangle$
cross-contractions, but the quartic contact invariant
$\mu_{\beta\gamma}=\langle\eta,m_3(\eta,\eta,\eta)\rangle=0$
by ghost-number rigidity. The tower terminates: depth~$4$, not
by Lie cancellation (Jacobi) but by an abelian grading mechanism.

\medskip\noindent\textbf{Bar cohomology.}\enspace
Growth rate $3^n$ (same exponential class as Virasoro).
Generating function: algebraic. The two-generator PBW spectral
sequence collapses at~$E_2$. Central charge:
$c_{\beta\gamma}(\lambda)=2(6\lambda^2-6\lambda+1)$; at
$\lambda=1$, $c=2$. Partner: the fermionic $bc$ system has
$c_{bc}(\lambda)=1-3(2\lambda-1)^2$, and $c_{\beta\gamma}+c_{bc}=0$
(verify: $\lambda=1$ gives $2+(-2)=0$).

\medskip\noindent\textbf{$R$-matrix.}\enspace
Proportional to the identity Casimir on the $\beta\gamma$-state
space; the spectral $R$-matrix factors through the ghost-number
grading. Tier~(b), class~$\mathbf{C}$.

\medskip\noindent\textbf{Averaging.}\enspace
$\kappa(\beta\gamma)=c_{\beta\gamma}/2=6\lambda^2-6\lambda+1$.
Koszul dual: $(\beta\gamma)^!=bc$ (bosonic/fermionic exchange).
Complementarity (free-field branch, sum $=0$; Virasoro branch
gives $13$): $\kappa(\beta\gamma)+\kappa(bc)=0$.
Shadow class $\mathbf{C}$; genus-$2$: loop$\circ$loop only
(contact termination, distinct from Gaussian collapse).

% ----- 7.5b Fermionic bc -----
\subsection*{7.5b.\quad Fermionic $bc$ system}

The fermionic partner of $\beta\gamma$: fields $b$ of weight
$\lambda$, $c$ of weight $1-\lambda$, both fermionic,
$b(z)c(w) \sim 1/(z-w)$ with anticommuting statistics. Central
charge $c_{bc}(\lambda) = 1 - 3(2\lambda - 1)^2$; verify
$c_{bc} + c_{\beta\gamma} = 0$ at $\lambda = 1$: $-2 + 2 = 0$;
at $\lambda = 2$: $-26 + 26 = 0$ (string ghost cancellation).
At $\lambda = 1/2$: $c_{bc} = 1$ (single Dirac fermion); at
$\lambda = 2$: $c_{bc} = -26$ (reparametrisation ghost).

\medskip\noindent\textbf{Ordered bar differential.}\enspace
The ordered bar has two generators $s^{-1}b$, $s^{-1}c$ in the
augmentation ideal. Fermionic statistics change the sign
structure: $[s^{-1}b | s^{-1}c] = -[s^{-1}c | s^{-1}b]$ at
the bar level because both generators are odd after
desuspension ($|s^{-1}b| = |b| - 1 = \lambda - 1$). At
degree $2$:
\[
d_{\barB}\bigl([s^{-1}b|s^{-1}c]\otimes\eta_{12}\bigr)
\;=\;\mathbf{1},
\]
identical to the $\beta\gamma$ formula (simple-pole OPE).
Higher-degree differentials vanish by the same ghost-number
grading mechanism as $\beta\gamma$.

\medskip\noindent\textbf{Bar cohomology and $R$-matrix.}\enspace
Growth rate $3^n$, generating function algebraic (same exponential
class). $r^{bc}(z) = r_\lambda^{bc}(z)$; Tier (b),
class $\mathbf{C}$.

\medskip\noindent\textbf{Averaging.}\enspace
$\kappa(bc_\lambda) = c_{bc}(\lambda)/2
= (1 - 3(2\lambda-1)^2)/2 = -(6\lambda^2 - 6\lambda + 1)
= -\kappa(\beta\gamma_\lambda)$.
Koszul dual: $(bc)^! = \beta\gamma$ (fermionic/bosonic exchange,
inverse of the $\beta\gamma$ duality). Complementarity
(free-field branch): $\kappa(bc) + \kappa(\beta\gamma) = 0$.
The $bc$/$\beta\gamma$ duality is the simplest instance of
bosonic/fermionic Koszul complementarity: it interchanges
commuting and anticommuting statistics while preserving the
OPE structure.

% ----- 7.6 Lattice -----
\subsection*{7.6.\quad Lattice vertex algebras}

Arithmetic laboratory: the shadow tower inherits the Gaussian
archetype from the Heisenberg factor; the braiding carries the
full arithmetic of the lattice. Curvature sees only rank;
braiding sees the quadratic form.

\medskip\noindent\textbf{Ordered bar differential.}\enspace
For an even lattice $\Lambda$ of rank~$N$, quadratic form~$q$,
$2$-cocycle~$\varepsilon$:
$V_\Lambda^{N,q}=\cH_1^{\otimes N}\otimes_\bC\bC[\Lambda]_\varepsilon$
(level $k=1$ from the lattice bilinear form).
The ordered bar decomposes as a tensor product of $N$ copies of
the Heisenberg ordered bar, tensored with the group algebra of
the lattice. At degree~$2$, the differential acts on each
Heisenberg factor independently:
\[
d_{\barB}\bigl([s^{-1}\alpha^i|s^{-1}\alpha^j]
\otimes\eta_{12}\bigr)
\;=\;\delta^{ij}\cdot\mathbf{1},
\]
producing the identity Casimir in the rank-$N$ current space.
The vertex operators $e^{\lambda\cdot\phi}$ contribute only
through the lattice cocycle $\varepsilon(\lambda,\mu)$, which
enters the ordering of tensor factors but not the collision
residue. All structure is captured at tensor degree~$2$:
the bar complex is quadratic.

\medskip\noindent\textbf{Bar cohomology.}\enspace
$H^1(\barB(V_\Lambda))$ has dimension~$N$ (the $N$ current
generators $\alpha^{i*}$); higher cohomology inherits the
Heisenberg vanishing $H^n=0$ for $n\ge 2$ in each tensor
factor, but the lattice group algebra contributes additional
classes through the vertex operator sector. The
partition-graded generating function is transcendental:
$\prod_{m\ge 1}(1-x^m)^{-N}$, the $N$-fold Fock-space grading.

\medskip\noindent\textbf{$R$-matrix.}\enspace
$r^{\Lambda}(z)=N/z$ (scalar, rank copies of Heisenberg
$r$-matrix at level $k=1$). Tier~(a); spectral $R$-matrix
$R(z)=\exp(N/z)$; Yang--Baxter trivial. The braiding
$\pi_1(\mathrm{Conf}_n(X))\to\mathrm{Aut}(V_\Lambda^{\otimes n})$
from the lattice $2$-cocycle is invisible to the $r$-matrix.

\medskip\noindent\textbf{Averaging.}\enspace
$\kappa(V_\Lambda^{N,q})=\mathrm{rank}(\Lambda)=N$,
independent of $\varepsilon$ and~$q$. Curvature-braiding
orthogonality: the curvature class
$[\kappa\cdot\omega_g]\in H^{1,1}(\overline\cM_g)$ and the
braiding representation act on complementary factors of the
state space. Shadow class $\mathbf{G}$; depth~$2$;
genus-$2$: loop$\circ$loop only.
Self-dual lattices ($E_8$: $N=8$; Leech: $N=24$) give
holomorphic VAs with trivial modular functor and theta-function
partition $\Theta_\Lambda/\eta^N$.

% ----- 7.7 Yangians -----
\subsection*{7.7.\quad Yangians and quantum groups}

The line-operator algebra. Yangian $Y(\fg)$ governs the
topological direction of a 3d HT theory; its $R$-matrix is the
genus-$0$ binary shadow of $\Theta$. Yang--Baxter is the
degree-$3$ MC equation; RTT encodes all degrees.

\medskip\noindent\textbf{$R$-matrix as genus-$0$ binary shadow.}
\[
r(z) \;=\; \Res^{\coll}_{0,2}(\Theta_\cA),
\qquad
R(z) \;=\; 1 + r/z + r^{(2)}/z^2 + \cdots.
\]
The classical Yang--Baxter equation
$[r_{12}, r_{13}] + [r_{12}, r_{23}] + [r_{13}, r_{23}] = 0$
is the Arnold relation on $\FM_3(\bC)$ evaluated on the
Casimir, and the three terms correspond to the three boundary
divisors of $\overline C_3(\bC)$.

\medskip\noindent\textbf{MC3 and all-types CG.} On the
type-$A$ Yangian surface the post-CG problem reduces to a
single compact/completed extension packet by (a) chromatic
filtration of $K_0(\Rep)$ by $q$-character support,
(b) prefundamental Clebsch--Gordan closure
$V_n \otimes L^- = \bigoplus_{j=0}^n L^-(n-2j)$ at the
character level, and (c) Francis--Gaitsgory pro-nilpotent
completion. The CG decomposition is extended to all simple
types via the Chari--Moura multiplicity-free $\ell$-weight
property (Theorem~\ref{thm:categorical-cg-all-types},
Corollary~\ref{cor:mc3-all-types}); the remaining post-CG
completion packets are open beyond type~$A$.

\medskip\noindent\textbf{dg-shifted Yangian.} The modular
dg-shifted Yangian
$Y_T^{\mod} = \varprojlim_r Y_T^{\mod,\le r}$ is the
pro-nilpotent completion of the convolution dg Lie algebra of
the 3d HT chiral algebra for $T$, and the modular $R$-matrix
$R_T^{\mod}(z;\hbar) \in \MC(Y_T^{\mod})$ is an MC element.
The Yang--Baxter equation is the degree-$3$ projection; the
higher RTT relations encode all degrees; the inverse limit
converges by Mittag-Leffler stabilisation.

\medskip\noindent\textbf{Drinfeld--Kohno.} The KZ connection
$\nabla_{\KZ} = d - \hbar\sum_{i<j} \Omega_{ij}\,dz_{ij}/z_{ij}$
on $\Conf_n(\bC)$ has monodromy that agrees with the
quantum-group representation category by the affine
Drinfeld--Kohno theorem; shadow-side this is the statement
$\nabla_{\KZ} = \mathrm{Sh}_{0,n}(\Theta_{\widehat\fg_k})$ on
the affine comparison surface.

\subsection*{7.8.\quad Drinfeld--Sokolov reduction as package morphism}

$\mathrm{DS}\colon \widehat{\mathfrak{sl}}_3{}_k \to \cW_{3,c(k)}$
with $c(k) = 2 - 24(k+2)^2/(k+3)$ extends to a morphism of
holographic data:
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lll}
& $\cH(\widehat{\mathfrak{sl}}_3{}_k)$
 & $\mathrm{DS}(\cH)$\\
\hline
$\cA$ & $\widehat{\mathfrak{sl}}_3{}_k$ & $\cW_{3,c(k)}$\\
$\cA^!$ & $\widehat{\mathfrak{sl}}_3{}_{-k-6}$ & $\cW_{3,100-c(k)}$\\
$r(z)$ & $k\,\Omega_{\mathfrak{sl}_3}/z$ & $r_c^{W_3}(z)$\\
$\kappa$ & $4(k+3)/3$ & $5c(k)/6$\\
depth & $3$ & $\infty$\\
$\Theta^{(2)}_{\mathrm{pf}}$ & $0$ & $\neq 0$
\end{tabular}
\end{center}
The Casimir $r$-matrix $k\Omega/z$ specialises to
$r_c^{W_3}(z)$; the curvature shifts; the shadow depth jumps
$3 \to \infty$; the planted-forest shell activates. At the
critical level $k = -3$: $\kappa \to 0$ on the affine side,
$c \to \infty$ on the $\cW_3$ side (Sugawara pole).

The DS-HPL transfer theorem (Volume II) makes the chain-level
mechanism precise. Homological perturbation through the BRST
SDR transfers the affine dg-shifted Yangian triple
$(m, r, \Delta)$ to the $\cW$-algebra side: the $A_\infty$
products transfer with nontrivial quartic pole (infinite
degree); the $r$-matrix transfers with the expected pole-order
shift; the coproduct is annihilated by a ghost-number
obstruction, so $\Delta_z^\cW = 0$ at all degrees. Gravity
does not produce particles, only braids them. Central-charge
additivity: the central charge difference
$c(\widehat{\fsl}_3{}_k) - c(\cW_3, k) = 6(4k{+}5)$
%: Fateev-Lukyanov formula. OLD WRONG: k-independent c_ghost=6.
is $k$-dependent (it includes both the free ghost $bc$ central charge
and the BRST stress-tensor improvement).

\subsection*{7.9.\quad Geometric localization principle}

Drinfeld--Sokolov reduction is Hamiltonian reduction from
$J_\infty(\fg^*)$ to $J_\infty(S_f)$, where $S_f = f + \fg^e$
is the Slodowy transverse slice to the nilpotent orbit of $f$.
The Slodowy slice meets every orbit transversally, carries a
Kirillov--Kostant Poisson structure, and its quantisation is
the finite $W$-algebra (Gan--Ginzburg, Premet). The chiral
upgrade replaces $S_f$ by its arc space, and
$\gr_F \cW^k(\fg, f) \cong \bC[J_\infty(S_f)]$.

In this reading: the PBW--Slodowy collapse is smoothness of
the Slodowy slice; the shadow depth jump $3 \to \infty$
under DS records the nonlinearity of the Dirac bracket on
$J_\infty(S_f)$; Barbasch--Vogan orbit duality
$f \leftrightarrow f^D$ is Springer duality of Slodowy slices,
and curvature complementarity is an algebraic identity under
the Feigin--Frenkel involution; the master commutative square
(Theorem~\ref{thm:master-commutative-square}) organises the
whole picture, with bar complexes on the upper row and
Hamiltonian reduction on arc spaces on the lower row.

\subsection*{7.10.\quad The $\mathfrak{gl}_N$ chiral quantum
group tower}

The chiral quantum group programme covers the full
$\mathfrak{gl}_N$ tower. For every $N \ge 1$, the principal
$\cW$-algebra $\cW_N$ carries a chiral quantum group datum: the
Yang $R$-matrix $R(u) = u\,I + \Psi\,P$ (where $\Psi$ is the
deformation parameter and $P$ is the permutation matrix), the
Drinfeld coproduct $\Delta_z(T(u)) = T(u)\cdot T(u{-}z)$ as
$N \times N$ matrix multiplication, and nontrivial RTT relations
for $N \ge 2$. The universal Miura coefficient $(\Psi{-}1)/\Psi$
on all cross-terms $J \otimes W_{s-1}$ persists at every spin
$s \ge 2$: the coproduct corrections are determined by a single
structural coefficient from the Prochazka--Rapcak Miura
factorization. Concrete verifications: $N = 2$ (explicit
$4 \times 4$ $R$-matrix), $N = 3$ ($9 \times 9$, all $81$
component RTT relations, quantum determinant centrality with
decreasing column ordering).

At integer level $k$, ordered chiral homology recovers the
Verlinde formula: $Z_g = \sum_j S_{0j}^{2-2g}$ as the dimension
of ordered chiral homology at level~$k$ with $n = k+2$. Closed-form
polynomials $P_g(n) = n^{g-1}(n^2{-}1)\cdot R_{g-2}(n^2)$ are
proved through genus~$6$; the leading coefficient
$[n^{3g-3}]P_g = \zeta(2g{-}2)/(2^{g-2}\pi^{2g-2})$ connects
the Verlinde tower to values of the Riemann zeta function at even
positive integers.

\medskip\noindent\textbf{The $\mathfrak{gl}_N$ tower in detail.}\enspace
The tower is controlled by the Miura factorisation
$T(u) = \prod_{i=1}^N (u + \Lambda_i)$, where $\Lambda_i$ are
the free-boson momenta in the Miura representation. The elementary
symmetric polynomials $\psi_s = e_s(\Lambda_1, \ldots, \Lambda_N)$
generate $\cW_N$; the coproduct is multiplicative in $T(u)$:
\[
\Delta_z(T(u)) \;=\; T(u) \cdot T(u - z),
\]
where the product is $N \times N$ matrix multiplication in the
generating-matrix formalism of RTT. The coefficient of
$:J \cdot W_{s-1}:$ in the coproduct at spin $s$ is
$(\Psi - 1)/\Psi$ at all $s \ge 2$: this universality is
proved by a three-step argument from the Miura decomposition:
(1)~the single-$J$ sector produces $1/\Psi$ from the elementary
symmetric expansion; (2)~the Drinfeld shift $u \mapsto u - z$
adds $+1$; (3)~lower sectors with $\ge 2$ factors of $J$ do not
contribute at linear order. The coefficient
$(\Psi - 1)/\Psi$ agrees with $1/\Psi$ only at $\Psi = 2$;
three-point verification at $\Psi = 1, 2, 3$ eliminates the
coincidence.

The RTT relations encode commutation of $T$-matrix entries:
$R(u_1 - u_2) T_1(u_1) T_2(u_2) = T_2(u_2) T_1(u_1) R(u_1 - u_2)$,
with $R(u) = u\,I + \Psi\,P$ (Yang's rational solution). At $N = 1$:
$T(u) = u + J$, the RTT relation is the Heisenberg commutation
$[J, J] = k$, and the $R$-matrix is scalar. At $N = 2$: the
$4 \times 4$ $R$-matrix produces four independent commutation
relations among $\{J, T\}$; the quantum determinant
$\mathrm{qdet}\,T(u) = T_{11}(u)T_{22}(u - \Psi) -
T_{12}(u)T_{21}(u - \Psi)$ is central. At $N = 3$: the quantum
determinant with \emph{decreasing} column ordering
\[
\mathrm{qdet}\,T(u)
\;=\;
\sum_{\sigma \in S_3} (-1)^{|\sigma|}
T_{1,\sigma(1)}(u) T_{2,\sigma(2)}(u - \Psi) T_{3,\sigma(3)}(u - 2\Psi)
\]
is central; increasing column ordering fails centrality at $N \ge 3$
(coincidental agreement at $N = 2$ masks the distinction). All $81$
component RTT relations are verified for $\mathfrak{gl}_3$.

The Drinfeld coproduct $\Delta_z$ is \emph{spectral coassociative}:
\[
(\Delta_{z_1} \otimes \id) \circ \Delta_{z_1 + z_2}
\;=\;
(\id \otimes \Delta_{z_2}) \circ \Delta_{z_1},
\]
with \emph{shifted} parameters (not $\Delta_z \circ \Delta_z$).
The Yang--Baxter equation for $R(u)$ is the degree-$3$ shadow of
coassociativity; the full RTT tower encodes all degrees.

\medskip\noindent\textbf{Stokes geometry.}\enspace
The KZ connection for $\cW_N$ has irregular singularity at $z = 0$
of Poincar\'e rank $2N - 2$, producing $4N - 4$ Stokes rays
(linear in $N$): the $W$--$W$ channel (pole order $2N$) dominates
the Stokes structure. At $N = 2$: $4$ Stokes rays (Virasoro).
At $N = 3$: $8$ rays. At $N = 4$: $12$ rays. The Stokes data
encode the connection matrices between asymptotic solutions of the
differential equation $\nabla_{\KZ}\Phi = 0$ and constitute the
nonperturbative completion of the perturbative shadow series.

\medskip\noindent\textbf{Antipode obstruction.}\enspace
The formal antipode $S(T(u)) = T(u)^{-1}$ (matrix inverse as
formal power series in $u^{-1}$) does NOT lift to a
vertex-algebraic antipode. Two independent obstructions:
(i)~the OPE obstruction:
$S(T)_{(3)}S(T) \neq c/2$ at generic $\Psi$, violating the
Virasoro Ward identity for the stress tensor; (ii)~the Hopf
axiom obstruction: a residual $z \cdot J$ term prevents
$m \circ (S \otimes \id) \circ \Delta_z = \eta \circ \epsilon$
from holding at the vertex-algebraic level. Source: the Miura
factorisation is \emph{nonlinear} (the product $T(u) \cdot T(u-z)$
mixes spins), and the antipode would require
inverting this nonlinearity, which the vertex algebra does not
support. This is a genuine structural obstruction, not a
computational difficulty.

\subsection*{7.11.\quad Verlinde recovery from ordered chiral homology}

The Verlinde formula, the enumeration of conformal blocks at
integer level, is recovered from the ordered bar complex. For
$\cA = V_k(\mathfrak{sl}_2)$ at positive integer level $k$,
set $n = k + 2$. The ordered chiral homology on a genus-$g$
surface $\Sigma_g$ has dimension
\[
Z_g \;=\; \dim \int^{\mathrm{ord}}_{\Sigma_g} V_k(\mathfrak{sl}_2)
\;=\; \sum_{j=0}^{k} S_{0j}^{2-2g},
\]
where $S_{0j} = \sqrt{2/n}\,\sin(\pi(j+1)/n)$ is the modular
$S$-matrix entry. The three sewing mechanisms (handle attachment,
separating factorisation, nonseparating factorisation) are
verified independently:
\begin{itemize}[nosep]
\item \emph{Handle attachment}: gluing a handle to $\Sigma_{g-1}$
multiplies the trace by $\sum_j S_{0j}^{-2}$, producing the
correct genus recursion $Z_g = (\sum_j S_{0j}^{-2}) \cdot Z_{g-1}$.
\item \emph{Separating factorisation}: cutting $\Sigma_g$ along a
separating circle recovers $Z_g = \sum_j Z_{g_1}^{(j)} Z_{g_2}^{(j)}$
with $g_1 + g_2 = g$.
\item \emph{Nonseparating factorisation}: cutting along a
nonseparating circle recovers the trace with insertion of the
Casimir.
\end{itemize}

The closed-form polynomials:
\begin{align*}
Z_2 &= n(n^2 - 1)/6,\\
Z_3 &= n^2(n^2 - 1)(n^2 + 11)/180,\\
Z_4 &= n^3(n^2 - 1)(2n^4 + 23n^2 + 191)/7560,\\
Z_5 &= n^4(n^2 - 1)(n^2 + 11)(3n^4 + 10n^2 + 227)/226800,\\
Z_6 &= n^5(n^2 - 1)(2n^8 + 35n^6 + 321n^4 + 2125n^2 + 14797)/2993760.
\end{align*}
General form: $P_g(n) = n^{g-1}(n^2 - 1) \cdot R_{g-2}(n^2)$
with $R_{g-2}$ a polynomial of degree $g - 2$ in $n^2$. At
$k = 1$ ($n = 3$): $Z_2 = 4$, $Z_3 = 40$, $Z_4 = 560$.

The rational generating function
$G_n(x) = \sum_{j=1}^{n-1} 1/(1 - a_j x)$ with eigenvalues
$a_j = n/(2\sin^2(\pi j/n))$ encodes all $Z_g$ simultaneously:
$Z_g = [x^{g-1}]\,G_n(x)$ for $g \ge 2$. The eigenvalues $a_j$
are the inverse squares of the modular $S$-matrix entries (up to
normalisation), providing a spectral decomposition of the
Verlinde numbers.

The leading coefficient:
$[n^{3g-3}]P_g = \zeta(2g-2)/(2^{g-2}\pi^{2g-2})$. At $g = 2$:
$\zeta(2)/(2^0 \pi^2) = (\pi^2/6)/\pi^2 = 1/6$, matching the
leading coefficient of $Z_2 = n^3/6 - n/6$. The Verlinde tower
is the integer shadow of the shadow obstruction tower: $Z_g$ is
a polynomial in the level (an integer parameter); $F_g$ is a
rational function of the central charge (a continuous parameter).
The two towers share the leading asymptotic but differ at
subleading order.

\subsection*{7.12.\quad Depth escalation: from class L to class M}

Drinfeld--Sokolov reduction is the depth escalation mechanism.
For $\fg = \mathfrak{sl}_N$ with principal nilpotent
$f = f_{\mathrm{prin}}$, the BRST reduction
$\cW_{N,c(k)} = H^0_{Q_{\DS}}(V_k(\mathfrak{sl}_N) \otimes F_{\mathrm{gh}})$
takes an affine Kac--Moody algebra (class $\mathbf{L}$,
shadow depth $3$) to a $\cW$-algebra (class $\mathbf{M}$,
shadow depth $\infty$). The depth jumps because the Dirac
bracket on the Slodowy slice $S_f = f + \fg^e$ is nonlinear:
the Poisson structure on $J_\infty(S_f)$ has polynomial brackets
of unbounded degree, generating the infinite shadow tower.

The escalation is controlled by the homological perturbation
lemma (HPL). The DS strong deformation retract
\[
\xymatrix{
(V_k(\fg) \otimes F_{\gh}, Q_{\DS})
\ar@<0.5ex>[r]^-{\pi} &
(\cW_{N,c(k)}, 0)
\ar@<0.5ex>[l]^-{\iota}
}
\]
with homotopy $h$ transfers the bar-complex data through
the BRST complex. The transferred structures:
\begin{enumerate}[label=(\roman*),nosep]
\item The $A_\infty$ products transfer with pole-order shift:
$m_k^{\cW}$ acquires contributions from $k$-fold nested BRST
contractions, generating the infinite tower. The quartic pole
from $:TT:$ (absent on the affine side) appears as
$m_4^{\cW} = \pi \circ m_2^{\fg} \circ (h \circ m_2^{\fg})^2 \circ \iota^{\otimes 4}$.
\item The $r$-matrix transfers with expected pole-order shift:
the Casimir $r$-matrix $k\,\Omega/z$ specialises to the
$\cW_N$ $r$-matrix, gaining higher-order poles from
the nonlinear field redefinition.
\item The coproduct is annihilated: a ghost-number obstruction
kills every HPL tree correction to $\Delta_z$, so the
transferred coproduct $\Delta_z^{\cW} = 0$ at all degrees.
Gravity does not produce particles, only braids them.
\end{enumerate}

\medskip\noindent\textbf{Central charge shift.}\enspace
The central charge transforms as
$c(\cW_{N,k}) = (N-1)(1 - N(N+1)(k+N)^{-2})$ (Fateev--Lukyanov).
The ghost central charge
$c_{\gh}(N,k) = c(\widehat{\mathfrak{sl}}_N{}_k) - c(\cW_{N,k})$
includes both the free ghost $bc$ contribution and the BRST
stress-tensor improvement; it is $k$-dependent (not $k$-independent
as one might expect from the free ghost alone).

The modular characteristic shifts accordingly:
$\kappa(\cW_{N,c}) = c \cdot (H_N - 1)$, where
$H_N = \sum_{j=1}^{N} 1/j$ is the $N$-th harmonic number.
At $N = 2$: $H_2 - 1 = 1/2$, so $\kappa(\cW_2) = c/2 = \kappa(\Vir)$.
At $N = 3$: $H_3 - 1 = 5/6$, so $\kappa(\cW_3) = 5c/6$.

\medskip\noindent\textbf{Complementarity under DS.}\enspace
The Koszul conductor transforms: $K(\cW_{N,c}) = \kappa(\cW_{N,c})
+ \kappa(\cW_{N,c^!})$ where $c^! = c(k^!)$ with
$k^! = -k - 2h^\vee$. For principal $\cW_N$:
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{llll}
$N$ & $K(\cW_N)$ & Self-dual $c$ & Shadow class\\ \hline
$2$ & $13$ & $c = 13$ & $\mathbf M$\\
$3$ & $250/3$ & $c = 50$ & $\mathbf M$\\
$4$ & $?$ & $?$ & $\mathbf M$\\
BP & $196$ & $k = -3$ & $\mathbf M$
\end{tabular}
\end{center}
The Koszul conductor is a global duality invariant, not a local
ghost constant: $K_{\mathrm{BP}} = 196$ records the full
$c(k) + c(-k-6)$ sum for the Bershadsky--Polyakov algebra, not any
single ghost number or grading shift.

\subsection*{7.13.\quad Master invariant table}

The complete family-by-family census of $E_1$ bar invariants:

\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lllllll}
\textbf{Family} & $\kappa$ & $K = \kappa + \kappa'$ & $r(z)$
 & Class & $d_{\mathrm{alg}}$ & $d_{\mathrm{gen}}$\\ \hline
$\cH_k$ & $k$ & $0$ & $k/z$ & $\mathbf G$ & $2$ & $2$\\
$V_k(\fg)$ & $\frac{\dim\fg(k+h^\vee)}{2h^\vee}$ & $0$
 & $k\,\Omega/z$ & $\mathbf L$ & $3$ & $3$\\
$\Vir_c$ & $c/2$ & $13$ & $\frac{c/2}{z^3}+\frac{2T}{z}$
 & $\mathbf M$ & $\infty$ & $3$\\
$\cW_{3,c}$ & $5c/6$ & $250/3$ & $r_c^{W_3}(z)$
 & $\mathbf M$ & $\infty$ & $3$\\
$\cW_{N,c}$ & $c(H_N{-}1)$ & family-dep & $r_c^{W_N}(z)$
 & $\mathbf M$ & $\infty$ & $3$\\
$\beta\gamma_\lambda$ & $6\lambda^2{-}6\lambda{+}1$ & $0$
 & $r_\lambda(z)$ & $\mathbf C$ & $4$ & $4$\\
$bc_\lambda$ & $-(6\lambda^2{-}6\lambda{+}1)$ & $0$
 & $r_\lambda^{bc}(z)$ & $\mathbf C$ & $4$ & $4$\\
$V_\Lambda$ & $\mathrm{rk}(\Lambda)$ & $0$ & $N/z$
 & $\mathbf G$ & $2$ & $2$\\
$\mathrm{BP}_k$ & $\mathrm{BP}(k)$ & $98/3$ & $r_k^{\mathrm{BP}}(z)$
 & $\mathbf M$ & $\infty$ & $?$\\
$\mathrm{SVir}_c$ & $(3c-2)/4$ & $?$
 & $r_c^{\mathrm{SVir}}(z)$ & $\mathbf M$ & $\infty$ & $?$
\end{tabular}
\end{center}

\noindent
Two depths are recorded: the algebraic depth $d_{\mathrm{alg}}$
(whether the shadow tower terminates) and the generating depth
$d_{\mathrm{gen}}$ (the degree at which all higher operations are
determined by lower ones). For Virasoro: $d_{\mathrm{gen}} = 3$
(the operation $m_3$ generates all $m_k$ recursively), but
$d_{\mathrm{alg}} = \infty$ (all $m_k$ are nonzero, so the tower
never terminates). The depth gap theorem: $d_{\mathrm{alg}} \in
\{0, 1, 2, \infty\}$ with gap at $3$ (no standard family has
$d_{\mathrm{alg}} = 3$ because the Jacobi identity on the shadow
Lie algebra forces either termination at degree $4$ or
propagation to all degrees).

The Bershadsky--Polyakov algebra $\mathrm{BP}_k = \cW^k(\mathfrak{sl}_3,
f_{\mathrm{min}})$ is the simplest non-principal $\cW$-algebra:
the level involution $k \mapsto -k-6$ has fixed point $k = -3$, which
coincides with the critical level $-h^\vee(\mathfrak{sl}_3) = -3$ where
$c(\mathrm{BP}_k)$ has a simple pole; the value $\kappa(-3) = 49/3$
is the \emph{principal-value symmetric limit} across the pole, not a
regular function value. The central-charge conductor is a polynomial
identity $c(k) + c(-k-6) \equiv 196$ in $\mathbb{Q}(k)$, and the induced
$\kappa$-conductor is $K = \varrho \cdot 196 = 98/3$ with
$\varrho = 1/6$. The conformal weight range is $\{1, 3/2, 2\}$
(a weight-$3/2$ field from the minimal nilpotent orbit, absent in
principal reductions). The super Virasoro algebra $\mathrm{SVir}_c$
has $\kappa = (3c-2)/4$ and an infinite shadow tower driven by the
superconformal self-coupling.


% ====================================================================
\section*{8.\quad Arithmetic of the shadow obstruction tower}
% ====================================================================

The shadow obstruction coefficients for the standard families are
rational functions of the central charge. Their denominators,
zeros, and growth rates carry number-theoretic information
connecting the shadow calculus to $L$-functions. What arithmetic
does the MC equation force?

\subsection*{The Dirichlet--sewing lift}

The genus-$1$ connected free energy $F_1^{\conn}(\cA;q) =
-\log\det(1 - K_q)$ encodes connected sewing amplitudes
$a_\cA(N)$ as Fourier coefficients. The Dirichlet--sewing lift
\begin{equation}\label{eq:preface-dirichlet-sewing-b}
S_\cA(u)
\;=\;
\sum_{N \ge 1} a_\cA(N) N^{-u}
\;=\;
\frac{(2\pi)^u}{\Gamma(u)}
\int_0^\infty F_\cA^{\conn}(e^{-2\pi y})\, y^{u-1}\, dy
\end{equation}
is a Dirichlet series whose analytic structure is controlled by
$\Theta_\cA$. The sewing amplitudes define an inner product
$\langle f, g\rangle_\cA = \sum_N a_\cA(N) f(N) g(N)$ with
reproducing kernel $K_\cA(s,t) = S_\cA(s+t)$; the surface
moment matrix
$\mathscr M_{ij} = K_\cA(\alpha/2 + i, \alpha/2 + j)$ is
positive definite for all $\alpha \ge 2$
(Theorem~\ref{thm:gram-positivity}), a Gram matrix $V^T D V$
with Vandermonde $V$.

Explicit values:
\[
\begin{aligned}
S_\cH(u) &= \zeta(u)\zeta(u+1),\\
S_{V_k(\fg)}(u) &= \dim(\fg)\cdot\zeta(u)\zeta(u+1),\\
S_{\Vir}(u) &= \zeta(u+1)(\zeta(u) - 1),\\
S_{\cW_N}(u) &= \zeta(u+1)\Bigl((N-1)\zeta(u)
- \textstyle\sum_{j=1}^{N-1} H_j(u)\Bigr),
\end{aligned}
\]
where $H_j(u) = \sum_{n=1}^j n^{-u}$ are partial harmonic sums.

\subsection*{The three-tier Euler--Koszul classification}

The \emph{Euler defect} $D_\cA(u) := S_\cA(u)/(|W(\cA)|\,\zeta(u)\,\zeta(u+1))$,
where $|W(\cA)|$ is the number of strong generators
($|W(\cH)|=1$, $|W(\widehat\fg_k)|=\dim\fg$, $|W(\beta\gamma)|=2$),
sorts chiral algebras:
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lll}
\textbf{Tier} & \textbf{Condition} & \textbf{Families}\\ \hline
Exact Euler--Koszul & $D_\cA(u) \equiv 1$
 & $\cH$, $V_k(\fg)$, $\beta\gamma$\\
Finitely defective & $1 - D_\cA(u)$ finite harmonic ratio
 & Virasoro, $\cW_N$\\
Non-Euler--Koszul & $S_\cA$ decomposes into Hecke $L$-functions
 & lattice VOAs with $h(D) \ge 2$
\end{tabular}
\end{center}
The Euler--Koszul class $\mathrm{ek}(\cA) = \max_i(w_i - 1)$
and the shadow depth $r_{\max}(\cA)$ are independent invariants
(Theorem~\ref{thm:shadow-euler-independence}): character
arithmetic and OPE interaction are logically independent axes.

\subsection*{The two-variable $L$-object}

Rankin--Selberg unfolding against $E^*(\tau, s)$ gives
\begin{equation}\label{eq:preface-two-variable-L-b}
L_\cA(s, u)
\;=\;
\int_\cF^{\mathrm{reg}} F_\cA^{\conn}(\tau) E^*(\tau, s) y^{u-2}\,dx\,dy.
\end{equation}
The \emph{sewing--Hecke reciprocity theorem} collapses both
variables to one: $L_\cA(s, u) = \Gamma(v)/(2\pi)^v\,S_\cA(v)$
with $v = s + u - 1$. The scattering poles of $E^*$ at
$s = \rho/2$ (nontrivial zeros $\rho$ of $\zeta$) are
\emph{not} poles of $L_\cA$; the nontrivial zeros appear as
structural obstructions to the Euler product, not as poles of
the $L$-object.

\subsection*{Shadow-moduli resolution}

The shadow-moduli map $t\colon \mathfrak H \to \bC$ solves
$\prod_j(1 - \lambda_j\,t(q))^{c_j} = \det(1 - K_q^{\conn})$
with spectral atoms $\lambda_j$ and multiplicities $c_j$. The
connected free energy factorises as $F_1^{\conn}(q) =
G_\cA(t(q))$ with
\[
G_\cA(t) \;=\; \int\log(1 - \lambda t)\,d\rho_\cA(\lambda),
\]
determined by the spectral measure alone
(Theorem~\ref{thm:universality-of-G}). The moments
$\mu_r = \int\lambda^r\,d\rho_\cA$ satisfy the MC recursion
\[
\mu_{r+1} \;=\; (r+1)\,\mathrm{Br}_{r+1}(\mu_2,\ldots,\mu_r;\cA)
\]
(the bar-recursion polynomial determined by the MC structure)
degree by degree. For two Satake atoms $\alpha, \beta$, the
Newton relations give the power sums
$p_r = e_1 p_{r-1} - e_2 p_{r-2}$, encoding the MC recursion
in spectral coordinates.

\subsection*{Interacting Gram matrix and resonance}

The shadow obstruction tower provides corrections to Gram
positivity. The interacting weight
$w_\cA(N;\alpha) = a_\cA(N)\cdot\prod_j(1 - \lambda_j N^{-\alpha/2})^{c_j}$
is unconditionally positive when all atoms $\lambda_j$ are
negative. For Virasoro with $c > 0$:
$\lambda_{\mathrm{eff}} = -6/c < 0$, so positivity holds
unconditionally for $\alpha \ge 2$. The resonance locus $\cR$
is empty for $c > 0$ and lies in $c < 0$, with the Lee--Yang
point $c = -22/5$ as the first entry.

\subsection*{The Weil analogy}

\begin{center}
\small
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{ll}
\textbf{Weil proof for $C/\bF_q$} & \textbf{MC equation for $\cA$}\\ \hline
Curve $C/\bF_q$ & chirally Koszul $\cA$\\
Frobenius $\mathrm{Frob}_q$ & MC element $\Theta_\cA = D_\cA - d_0$\\
$\mathrm{Frob}^2 = q$ & $D_\cA^2 = 0$\\
\'Etale cohomology $H^i_{\text{\'et}}$ & cyclic deformation $\Defcyc(\cA)$\\
Weight filtration & degree filtration $\Theta_\cA^{\le r}$\\
Eigenvalues $\alpha_i$ on $H^1$ & spectral atoms $\lambda_j$\\
$\|\alpha_i\| = q^{1/2}$ & $|a_{f_j}(p)| \le 2p^{(k-1)/2}$\\
Lefschetz $L$ & bracket with $\kappa(\cA)$
\end{tabular}
\end{center}
For even unimodular lattice VOAs $V_\Lambda$ with
$\Theta_\Lambda = c_E E_{r/2} + \sum_j c_j f_j$, the
Hecke--Newton closure gives: MC equation $\Rightarrow$
prime-local CG closure $\Rightarrow$ CPS automorphy
$\Rightarrow \Sym^{r-1}(f)$ $\Rightarrow$ Ramanujan bound.
Deligne's theorem supplies the bound itself; the MC framework
supplies the systematic Hecke decomposition.

\medskip\noindent\textbf{The key disanalogy.}\enspace
The Weil analogy is structural, not literal. The
principal difference: Weil's proof uses the Riemann hypothesis
for curves ($|\alpha_i| = q^{1/2}$ as \emph{equalities}); the
MC framework uses Ramanujan-type bounds
($|a_f(p)| \le 2p^{(k-1)/2}$ as \emph{inequalities}). The
passage from bound to equality would require a deeper structure:
a Langlands-type functoriality that promotes the MC framework from
an analogy to an equivalence. The shadow obstruction tower
provides the systematic input; the promotion is the open problem.

A second disanalogy: the weight filtration in the Weil setting
is a canonical, geometric invariant of the motive. The degree
filtration $\Theta_\cA^{\le r}$ is a choice of truncation, not
a canonical structure on $\gAmod$. Whether $\gAmod$ carries a
natural weight filtration (in the motivic sense) is a deep
question connecting the programme to mixed Hodge theory on
moduli spaces of stable curves.

A third disanalogy: in the Weil setting, the zeta function is a
single rational function. In the MC setting, the
two-variable $L$-object $L_\cA(s, u)$ is not manifestly rational
in either variable. Rationality in $u$ at fixed $s$ (or vice
versa) would be a structural theorem about the MC equation.

\subsection*{Polyakov--bar-cobar dictionary}

\begin{center}
\small
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{ll}
\textbf{Polyakov} & \textbf{Bar-cobar}\\ \hline
Conformal anomaly $(c/12)R$ & modular characteristic $\kappa$\\
$\det'_\zeta \Delta$ & Fredholm $\det(1 - K)$\\
Critical dimension $c = 26$ & dual curvature $\kappa(\Vir_{26-c}) = 0$\\
Ghost system $bc$ & Koszul dual $\cA^!$ (BRST pairing)\\
Genus expansion $Z = \sum g_s^{2g-2}Z_g$
 & MC5 sewing, $F_g = \kappa\lambda_g^{\FP}$ (uniform)\\
BPZ equations & shadow connection on comparison surface\\
Instanton sectors & Novikov-completed bar $B^\Lambda(\cA)$\\
Wilson line $\langle W(C)\rangle$ & Swiss-cheese boundary module
\end{tabular}
\end{center}
Anomaly, genus expansion, duality, critical dimension, and
non-perturbative completions all descend from
$\Theta_\cA \in \MC(\gAmod)$. The four depth classes
$\mathbf G/\mathbf L/\mathbf C/\mathbf M$ correspond to
increasing departures from the Gaussian path integral.

\subsection*{Arithmetic packet connection}

Hecke operators $T_p$ act on the space $M_\cA$ of activated
graph amplitudes $\ell_\Gamma^{(g)}$. Decompose
$M_\cA = \bigoplus_\chi M_\chi$ into Hecke generalised
eigenspaces with eigenvalue $a_\chi(p)$ and nilpotent part
$N_\chi$; attach to each eigenspace its packet function
$\Lambda_\chi(s)$ (completed $L$-function of the eigenform).
The \emph{arithmetic packet connection}
\[
\nabla_\cA^{\mathrm{arith}}
\;=\;
d \;-\; \bigoplus_\chi
\tfrac{\Lambda_\chi'(s)}{\Lambda_\chi(s)}
(\mathrm{id}_{M_\chi} + N_\chi)\,ds
\]
is flat (each block is scalar form times constant endomorphism).
The singular divisor $D_\cA$ is the zero-pole set of the packet
functions, depending only on the arithmetic skeleton
$M_\cA^{\mathrm{ss}}$.

The Eisenstein scattering function on $\cM_{1,1}$ is
$\varphi(s) = \Lambda^*(1-s)/\Lambda^*(s)$ with
$\Lambda^*(s) = \pi^{-s}\Gamma(s)\zeta(2s)$. The frontier
defect form
$\Omega_\cA = d\log\Lambda_{\mathrm{Eis}}(s) - d\log\varphi(s)$
vanishes iff the Eisenstein block is gauge-equivalent to the
scattering connection. For lattice VOAs at rank $r$,
$\Omega_{V_\Lambda} \neq 0$ in general because $\zeta(s)$ and
$\zeta(2s)$ have different zero sets.

\subsection*{Finite Miura defect}

The principal $\cW_N$ character is
$\chi_{\cW_N}(q) = \prod_{n \ge 2}
(1 - q^n)^{-\min(n-1, N-1)}$;
the Heisenberg character is
$\chi_\cH(q) = \prod_{n \ge 1}(1 - q^n)^{-1}$. The ratio is
finite:
\[
\chi_{\cW_N}(q)
\;=\;
\chi_\cH(q)^{N-1}
\cdot \prod_{m=1}^{N-1}(1 - q^m)^{N-m}.
\]
The finite product is the Miura defect; all genus-$1$
arithmetic content in $\cW_N$ beyond Heisenberg is carried by
it. The prime-side Dirichlet analogue is
$D_{\cW_N}^{\mathrm{prime}}(u) = -\zeta(u+1)
\sum_{m=1}^{N-1}(N - m)m^{-u}$; the packet connection splits
into $(N-1)$ Heisenberg copies plus a defect governing modes
$m = 1, \ldots, N - 1$.

\subsection*{Quartic closure programme}

The quartic resonance class
$\mathfrak{R}_{4,g,n}^{\mod}(\cA)$ satisfies a clutching law
along every separating stratum
\[
\xi^*\mathfrak{R}_{4,g,n}^{\mod}
\;=\;
p_1^*\mathfrak{R}_{4,g_1,n_1+1}^{\mod}
+ p_2^*\mathfrak{R}_{4,g_2,n_2+1}^{\mod}
+ \mathfrak{T}_{3,\xi}
\]
(Theorem~\ref{thm:nms-clutching-law-modular-resonance}). The
$3 \times 3$ Schur complement of the mixed $(s,u)$-transform
extracts the quartic contact potential $S_4(\cA)$ on the potential side and its
reciprocal on the Gram side. For Virasoro:
$S_4(\Vir_c) = 10/[c(5c+22)]$.

Three closure conjectures form a hierarchy (each implies its
predecessors): \emph{quartic closure} (intersection of Gram
loci equals $\{\Re\rho = 1/2\}$,
Conjecture~\ref{conj:quartic-closure}),
\emph{Beilinson closure} (global discrepancy
$\cB^{\mathrm{glob}}(\rho)$ vanishes iff $\Re\rho = 1/2$,
Conjecture~\ref{conj:beilinson-closure}), and
\emph{clutching closure} (residue clutching defect
$K_{\cA,\rho,\xi}$ vanishes for all families iff
$\Re\rho = 1/2$, Conjecture~\ref{conj:clutching-closure}).
The chain of constructions
$\Theta_\cA \to w_{c,\rho,u_0} \to$ Gram matrix $\to$ Schur
complement $\to$ quartic resonance divisor $\to$ residue
clutching defect $\to$ closure conjecture is proved up to the
final link, which is conjectural.

\subsection*{Constrained Epstein zeta}

For a lattice VOA $V_\Lambda$ of rank $r$, the constrained
Epstein zeta
$\varepsilon^c_s(V_\Lambda) = \sideset{}{'}\sum_{\ell \in
\Lambda^{\bar}}\|\ell\|^{-2s}$
restricts the Epstein series to the sublattice
$\Lambda^{\bar} \subset \Lambda$ determined by the bar complex.
For the rank-$1$ lattice at self-dual radius $R = 1$, every
nonzero integer contributes:
$\varepsilon^1_s(R{=}1) = 4\zeta(2s)$. The simplest lattice
VOA's constrained Epstein zeta is the Riemann zeta.

The Hecke decomposition:
$\varepsilon^r_s(V_\Lambda) = \sum_j c_j L(s, \chi_j)$. Shadow
depth $d$ contributes $d - 1$ critical lines to the
meromorphic continuation, one for each degree stratum beyond
the Gaussian base. The nontrivial zeros of the component
$L$-functions are the scattering resonances of the hyperbolic
Laplacian on $\cM_{1,1}$: frequencies at which the genus-$1$
sewing amplitude fails to decay.

\medskip\noindent\textbf{Genus-$2$ B\"ocherer bridge.}
For the Leech lattice VOA, the Siegel modular form
$\chi_{12} = \mathrm{SK}(f_{22})$ is the Saito--Kurokawa lift
of the unique weight-$22$ cuspidal eigenform, and the
MC-derived second Fourier coefficient $c_2 \approx
-1.918 \times 10^{-6} \neq 0$ is the first nonzero central
$L$-value produced by the shadow obstruction tower,
connecting $\Theta_\cA$ to genus-$2$ Siegel modular forms via
the Furusawa--Morimoto theorem.

\subsection*{8.8.\enspace Verlinde polynomials from ordered
chiral homology}

At integer level $k$, ordered chiral homology recovers the
Verlinde formula
$Z_g = \sum_j S_{0j}^{2-2g}$ as the dimension of ordered
chiral homology of~$V_k(\mathfrak{sl}_2)$ with $n = k+2$.
The Verlinde numbers are polynomials in~$n$:
\begin{align*}
Z_2 &= n(n^2-1)/6, \\
Z_3 &= n^2(n^2-1)(n^2+11)/180, \\
Z_4 &= n^3(n^2-1)(2n^4+23n^2+191)/7560,
\end{align*}
with general form $P_g(n) = n^{g-1}(n^2{-}1) \cdot
R_{g-2}(n^2)$ proved through genus~$6$. The leading
coefficient $[n^{3g-3}]P_g = \zeta(2g{-}2)/
(2^{g-2}\pi^{2g-2})$ connects the Verlinde tower to values
of the Riemann zeta function at even positive integers:
the arithmetic of level-$k$ conformal blocks encodes zeta
values. The rational generating function
$G_n(x) = \sum_j 1/(1 - a_j x)$ with
$a_j = n/(2\sin^2(\pi j/n))$ gives a closed form for
all~$Z_g$ simultaneously.

The Verlinde numbers $Z_g$ (integer, bundle ranks) are
distinct from the shadow free energies $F_g$ (rational, shadow
obstruction coefficients). At $k = 1$, $g = 2$:
$Z_2 = 4$ versus $F_2 = 7/2560$. The two towers have
different analytic behaviour: $Z_g$ is polynomial in $n$
(the level); $F_g$ is rational in the central charge $c$
(a continuous parameter).

\subsection*{8.9.\enspace The depth decomposition of the Dirichlet series}

The Dirichlet--sewing lift $S_\cA(u)$ admits a decomposition
indexed by the shadow depth classes:
\begin{enumerate}[label=(\roman*),nosep]
\item \emph{Gaussian stratum} ($r = 2$): $S_\cA^{(2)}(u) =
\kappa(\cA)\cdot\zeta(u)\zeta(u+1)$. This stratum is universal:
it depends only on the modular characteristic $\kappa$ and
reproduces the Heisenberg answer for all families. For
$\cH_k$: $S_\cH = S_\cH^{(2)}$, the full series is
exhausted by the Gaussian stratum.
\item \emph{Lie stratum} ($r = 3$): $S_\cA^{(3)}(u)$ carries
the Chevalley--Eilenberg contribution from the cubic shadow
$\mathfrak{C}(\cA)$. For affine Kac--Moody:
$S_{\widehat\fg_k}^{(3)}(u)$ encodes the Serre-relation
corrections to the Gaussian base.
\item \emph{Contact stratum} ($r = 4$): $S_\cA^{(4)}(u)$
records the quartic contact shadow
$\mathfrak{Q}(\cA)$. For $\beta\gamma$: the series terminates
here.
\item \emph{Mixed strata} ($r \ge 5$): for Virasoro and
$\cW_N$, infinitely many strata contribute. Each adds
$d - 1$ critical lines to the meromorphic continuation.
\end{enumerate}
The decomposition $S_\cA(u) = \sum_{r \ge 2} S_\cA^{(r)}(u)$
converges absolutely for $\Re(u) > 2$; the individual strata
have distinct analytic continuations, and their interaction is
governed by the MC equation: the compatibility
$[D_0, D_1] = 0$ between the genus-$0$ and genus-$1$
differentials forces cancellations among strata that would
individually produce spurious poles.

The Euler defect inherits this stratification:
$D_\cA(u) = 1 + \sum_{r \ge 3} D_\cA^{(r)}(u)$, with
$D_\cA^{(r)}$ the depth-$r$ correction. For Virasoro:
$D_{\Vir}(u) = 1 - 1/\zeta(u)$, the correction is the
reciprocal of the Riemann zeta function. For $\cW_3$:
$D_{\cW_3}(u) = 1 - (1 + 2^{1-u})/\zeta(u)$, with the
extra $2^{1-u}$ from the weight-$3$ generator.

\subsection*{8.10.\enspace Verlinde--shadow bridge}

The Verlinde polynomials $P_g(n)$ and the shadow free energies
$F_g(c)$ are distinct objects with a precise bridge. At level
$k$ with $n = k + 2$ and $c(k) = 3k/(k+2)$ for
$\mathfrak{sl}_2$:
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lll}
\textbf{Verlinde} & \textbf{Shadow} & \textbf{Bridge}\\ \hline
$Z_g = P_g(n)$ & $F_g = F_g(c)$ & $Z_g = Z_g^{\mathrm{pert}}
+ Z_g^{\mathrm{nonpert}}$\\
polynomial in $n$ & rational in $c$ & perturbative${}+{}$instanton\\
integer (rank of bundle) & rational (graph sum) & Verlinde
$\supset$ shadow\\
all levels & continuous $c$ & evaluates at discrete $k$\\
\end{tabular}
\end{center}
The perturbative part $Z_g^{\mathrm{pert}}$ is the shadow
evaluation at $\kappa = 3(k+2)/4$; the nonperturbative part
$Z_g^{\mathrm{nonpert}}$ comes from the finite sum over
integrable representations (a sum over $n - 1$ terms, not a
continuous integral). The shadow free energy $F_g(c)$ is the
perturbative shadow obstruction coefficient and agrees with
$Z_g^{\mathrm{pert}}$ when $c$ is specialised to $c(k)$. The
nonperturbative contribution is invisible to the shadow tower:
it requires the full ordered chiral homology, not just its
Taylor-coefficient extraction.

The leading asymptotics agree:
$P_g(n) \sim n^{3g-3} \cdot \zeta(2g-2)/(2^{g-2}\pi^{2g-2})$
for large $n$ matches
$F_g(c) \sim c^{g-1} \cdot \lambda_g^{\FP}$ for large $c$
(where $c \sim 3n/2$ for $\mathfrak{sl}_2$), because the
perturbative expansion dominates at large level.

\subsection*{8.11.\enspace Constrained Epstein zeta: depth decomposition}

The constrained Epstein zeta for rank-$r$ lattice VOAs admits a
parallel depth decomposition. For an even unimodular lattice
$\Lambda$ of rank $r$, the constrained series
\[
\varepsilon^r_s(V_\Lambda)
\;=\;
\sideset{}{'}\sum_{\ell \in \Lambda^{\bar}}
\|\ell\|^{-2s}
\]
splits by shell:
$\varepsilon^r_s = \varepsilon^r_{s,\mathrm{Gauss}}
+ \varepsilon^r_{s,\mathrm{arith}}$.
The Gaussian part is $r \cdot \zeta(2s)$ (rank copies of the
simplest constrained zeta). The arithmetic part
$\varepsilon^r_{s,\mathrm{arith}}$ is the Hecke-eigenvalue
decomposition
$\sum_j c_j L(s, \chi_j)$, with $\chi_j$ running over Hecke
characters attached to the lattice.

For the $E_8$ lattice ($r = 8$): the constrained Epstein
zeta is $\varepsilon^8_s(E_8) = 8\zeta(2s) + 480 L(s, \Delta_{16})$,
where $\Delta_{16}$ is the unique normalised cuspidal eigenform
of weight $16$ for $\mathrm{SL}_2(\bZ)$. The coefficient $480$
is the number of roots of $E_8$; the cuspidal component carries
the arithmetic beyond the Gaussian base.

For the Leech lattice ($r = 24$): the decomposition
$\varepsilon^{24}_s(\Lambda_{24}) = 24\zeta(2s)
+ c_{22}L(s, \Delta_{22}) + \cdots$
involves the weight-$22$ cusp form $\Delta_{22}$ and finitely
many additional Hecke eigenspaces. The B\"ocherer bridge
connects the genus-$2$ coefficient to the central $L$-value
$L(1/2, \Delta_{22} \times \chi_D)$.

The functional equation
$\varepsilon^r_s(V_\Lambda) = \varepsilon^r_{r/2-s}(V_\Lambda)$
(from the Poisson summation formula on the lattice) is the
Epstein analogue of the MC complementarity $\kappa + \kappa' = K$.
At the self-dual point $s = r/4$: the constrained zeta
evaluates to $\varepsilon^r_{r/4} = r \cdot \zeta(r/2)
+ \text{cuspidal contribution}$, connecting the complementarity
constant $K = 0$ (for lattice VOAs in the free-field branch)
to the trivial functional equation of $\zeta(r/2)$.


% ====================================================================
% TRACK A: section 9 (scalar saturation and the Koszulness programme)
% ====================================================================

\section*{9.\quad Scalar saturation and the Koszulness programme}
% ====================================================================

The bar construction works for all chiral algebras. It works best,
the cobar inverts the bar, the spectral sequence collapses, the
resolution is linear, precisely on the Koszul locus. Characterizing
this locus is the central foundational question introduced in~\S3.3
and anticipated throughout sections~4 and~5. Two complementary
results: scalar saturation (the MC element is determined by a single
scalar for all standard families) and the Koszulness meta-theorem
(fourteen characterisations: ten unconditionally equivalent, one
conditional on perfectness, one one-directional, plus the bifunctor
decomposition and the Sklyanin Poisson $H^2 = 0$ criterion).

\subsection*{9.1.\enspace Scalar saturation}

For a one-parameter algebraic family $\cA_k$ with rational OPE
coefficients (structure constants rational functions of~$k$), the
universal MC element satisfies
\[
\Theta_{\cA_k}=\kappa(\cA_k)\cdot\eta_{\mathrm{univ}}\otimes\Lambda_{\mathrm{univ}}+(\text{terms in }F^3\mathfrak g^{\mathrm{mod}}_{\cA_k}).
\]
\emph{Scalar saturation universality}: higher-order terms vanish. For
every algebraic family with rational OPE coefficients, $\Theta_{\cA_k}$
is determined by $\kappa(\cA_k)$ modulo terms in the degree-$\ge 3$
filtration.

\medskip
\noindent\textbf{Step~1: Whitehead reduction.}\enspace
For a vertex algebra with reductive symmetry at generic level, the
primitive cyclic cohomology
$H^2_{\mathrm{cyc,prim}}(\mathfrak g^{\mathrm{mod}}/F^3,d_2)$ is
computed by a Whitehead-type spectral sequence with
$E_2^{p,q}=H^p(\mathfrak g;\operatorname{Sym}^q V)$. For reductive
$\mathfrak g$ and generic level, $H^2(\mathfrak g;\operatorname{Sym}^q V)=0$
by the Whitehead lemma, and the degree-$2$ MC class lifts uniquely.

\medskip
\noindent\textbf{Step~2: Algebraic semicontinuity.}\enspace
The vanishing locus
\[
E=\{k\in\mathbb C:H^2_{\mathrm{cyc,prim}}(\cA_k)\neq 0\}
\]
is Zariski-closed by upper semicontinuity. At $k=\infty$ the algebra
is Heisenberg and $H^2_{\mathrm{cyc,prim}}=0$, so $E$ is a proper
Zariski-closed subset. Explicit computation verifies $E=\varnothing$
for $\mathfrak{sl}_N$ ($N=2,\ldots,10$): no exceptional level. The
result covers the entire standard Lie-theoretic landscape at all
non-critical levels, including admissible.

\medskip
\noindent\textbf{Scope.}\enspace
Scalar saturation applies to every family in the standard landscape:
affine Kac--Moody (all types, all non-critical levels), Virasoro (all
$c$), $\mathcal W_N$ (all $N$, all non-degenerate levels),
$\beta\gamma$ and lattice algebras (all parameters). The residual
conjecture, that $E=\varnothing$ for every positive-energy chiral
algebra with rational OPE coefficients, is open only for
non-algebraic-family constructions.

\subsection*{9.2.\enspace The Koszulness meta-theorem}

The Koszul condition admits twelve formulations, spanning homological
algebra (PBW collapse, Ext vanishing), homotopy theory ($A_\infty$
formality, $E_2$ formality), operadic algebra
(Barr--Beck--Lurie, FM acyclicity), modular geometry (FH
concentration, tropical Koszulness), and symplectic topology
(Lagrangian criterion). Ten are unconditionally equivalent; one (the
Lagrangian criterion) is conditional on perfectness/nondegeneracy;
one ($\mathcal D$-module purity) is one-directional (forward direction
proved, converse open).

\begin{center}
\emph{For $\cA$ positive-energy and finitely strongly generated, the
following are equivalent:}
\end{center}

\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item $\cA$ is chirally Koszul.
\item The PBW spectral sequence on $\barB^{(g)}(\cA)$ collapses at $E_2$ for every $g$.
\item The minimal $A_\infty$-model of $\barB(\cA)$ (the transferred structure on $H^\bullet$) is formal: $m_n=0$ for $n\ge 3$.
\item $\operatorname{Ext}^{p,q}_\cA(\omega_X,\omega_X)=0$ for $p\neq q$.
\item The bar-cobar counit $\Omega(\barB(\cA))\to\cA$ is a quasi-isomorphism.
\item The Barr--Beck--Lurie comparison for $\barB\dashv\Omega$ is an equivalence.
\item $\int_X\cA$ is concentrated in degree~$0$ for every smooth proper $X$.
\item $\operatorname{ChirHoch}^*(\cA)$ vanishes outside degrees $\{0,1,2\}$.
\item The Kac--Shapovalov determinant $\det G_h\neq 0$ in the bar-relevant range.
\item The restriction $i_S^!\barB_n(\cA)$ to every FM boundary stratum $S$ is acyclic outside degree~$0$.
\end{enumerate}

\noindent
Under the additional hypothesis that the ambient tangent complex is
perfect and nondegenerate:

\begin{enumerate}[label=\textup{(\roman*)},nosep,start=11]
\item $\mathcal M_\cA$ and $\mathcal M_{\cA^!}$ are transverse Lagrangians in the $(-1)$-shifted symplectic deformation space $\mathcal M_{\mathrm{comp}}$.
\end{enumerate}

\noindent
Finally (xii)$\Rightarrow$(x), where:

\begin{enumerate}[label=\textup{(\roman*)},nosep,start=12]
\item Each $\barB_n(\cA)$ is pure of weight~$n$ as a mixed Hodge module, with characteristic variety aligned to FM boundary strata ($\mathcal D$-module purity).
\end{enumerate}

\noindent The converse of (xii) is open.

\medskip
\noindent\textbf{The proof circuit.}\enspace
The core equivalence chain is
(i)$\Leftrightarrow$(ii)$\Leftrightarrow$(iii)$\Leftrightarrow$(v)$\Leftrightarrow$(viii),
proved by PBW concentration $\to$ bar-cobar inversion $\to$ chiral Hochschild
polynomial growth $\to$ Koszul-complex acyclicity, with the $A_\infty$
formality branch via HPL transfer and Keller classicality. From this
core: (iv) by Ext spectral sequence, (vi) by conservativity with
log-FM totalization, (vii) by $\barB=\int_X$, (ix) by non-degeneracy
forcing PBW injectivity, (x) by stratum-by-stratum PBW concentration.
The Lagrangian criterion (xi) uses PTVV derived intersection theory
on the perfectness hypothesis. The $\mathcal D$-module purity
implication (xii)$\Rightarrow$(x) uses weight filtration on the bar
complex; the converse would require concentration to force purity.
The cycle closes via (viii)$\Rightarrow$(i): Koszul-complex acyclicity
implies the defining characterisation.

\medskip
\noindent\textbf{Beyond the meta-theorem.}\enspace
Six additional characterisations are proved in the text:

\begin{enumerate}[label=\textup{(\alph*)},nosep]
\item \emph{Shadow-formality at low degree.} The shadow obstruction tower $\Theta^{\le r}_\cA$ equals the $L_\infty$-formality obstruction tower of $\mathfrak g^{\mathrm{mod}}_\cA$ at degrees $r=2,3,4$
(Proposition~\ref{prop:shadow-formality-low-degree}). Full equivalence to~(iii) requires all degrees.

\item \emph{$E_2$-formality of chiral Hochschild cohomology.} Koszulness implies $\operatorname{ChirHoch}^*(\cA)$ is formal as an $E_2$-algebra (Deligne conjecture applied to the bar-cobar resolution).

\item \emph{Genus-$0$ curve independence.} Koszulness on $\mathbb P^1$ implies Koszulness on every smooth proper curve (Proposition~\ref{prop:genus0-curve-independence}). Proved independently by factorization descent.

\item \emph{PBW universality} (sufficient). Every freely strongly generated vertex algebra is chirally Koszul (Proposition~\ref{prop:pbw-universality}). Applies to universal algebras: $V_k(\mathfrak g)$ is Koszul at every level including critical and admissible. For simple quotients $L_k(\fg)$ at admissible levels, status is rank-dependent: $L_k(\mathfrak{sl}_2)$ is Koszul at all admissible levels, but at $\operatorname{rk}(\fg)\ge 2$ with denominator $q\ge 3$, Koszulness fails via a $\operatorname{rk}(\fg)$-dimensional bar obstruction from the abelian Cartan
(Conjecture~\ref{conj:admissible-koszul-rank-obstruction}). PBW universality is one-directional: not every Koszul algebra is freely strongly generated.

\item \emph{Tropical Koszulness.} $\cA$ is chirally Koszul iff $\barB^{\mathrm{trop}}(\cA)$ is acyclic. Proved by the weight spectral sequence on the real blowup.

\item \emph{Bifunctor obstruction decomposition} (one-directional). Koszulness implies the RNW one-slot obstruction decomposes into independent bar-side and cobar-side components
(Theorem~\ref{thm:bifunctor-obstruction-decomposition}). The converse is open.
\end{enumerate}

\medskip
\noindent\textbf{Status summary.}
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{clll}
\multicolumn{4}{l}{\emph{Meta-theorem (Theorem~\ref{thm:koszul-equivalences-meta}):}}\\[1pt]
& (i)--(x) & \textbf{10 unconditional equivalences} & proved\\
& (xi) Lagrangian & conditional on perfectness & proved (unconditional for standard landscape)\\
& (xii) $\mathcal D$-module purity & (xii)$\Rightarrow$(x) only & converse open\\[3pt]
\multicolumn{4}{l}{\emph{Additional characterisations:}}\\[1pt]
& (a) Shadow-formality & equivalence at degrees $2,3,4$ & proved\\
& (b) $E_2$-formality & consequence of Koszulness & proved\\
& (c) Curve independence & independent theorem & proved\\
& (d) PBW universality & sufficient condition & proved\\
& (e) Tropical Koszulness & equivalence & proved\\
& (f) Bifunctor decomposition & one-directional & converse open
\end{tabular}
\end{center}

\subsection*{9.3.\enspace Shadow depth and operadic complexity}

The four depth classes G/L/C/M admit refinement: in general
$r_{\max}\in\{2,3,4,5,\ldots\}\cup\{\infty\}$, with class $\mathbf F_r$
(tower terminates at degree~$r$) structurally permitted for all
$r\ge 2$; $\mathbf G=\mathbf F_2$, $\mathbf L=\mathbf F_3$,
$\mathbf C=\mathbf F_4$ name the standard-landscape representatives.

\medskip
\noindent\textbf{The operadic complexity theorem}
(Theorem~\ref{thm:operadic-complexity-detailed}):
\[
r_{\max}(\cA)=A_\infty\text{-depth}(\cA)=L_\infty\text{-formality level}(\mathfrak g^{\mathrm{mod}}_\cA).
\]
$A_\infty$-depth is the minimal $r$ with $m_k=0$ for $k>r$ on
$H^\bullet(\barB(\cA))$; $L_\infty$-formality level is the minimal $r$
such that the $L_\infty$-structure on $\mathfrak g^{\mathrm{mod}}_\cA$
is formal through degree~$r$. Three consequences: the shadow
obstruction tower \emph{is} the $L_\infty$-formality obstruction
tower; the depth classification becomes a structural invariant of the
operadic type of $\cA$; the tower of a Gaussian algebra is a quadratic
form, of a Lie algebra a Chevalley--Eilenberg complex, of a contact
algebra a cyclic $A_\infty$-structure, of a mixed algebra an infinite
$L_\infty$-tower with no polynomial truncation.

The programme extends to non-principal $\mathcal W$-algebras: the
Bershadsky--Polyakov algebra $\mathrm{BP}_k$ is chirally Koszul at generic level ($k \neq -3$) with
dual $\mathrm{BP}_{-k-6}$ and Koszul conductor
$K_{\mathrm{BP}}=196$ (a global duality invariant, not
a local ghost constant). Nilpotent transport from hook-type seeds
covers all orbits in $\mathfrak{sl}_2$ through $\mathfrak{sl}_8$.

\subsection*{9.4.\enspace The PBW spectral sequence}

The computational engine for bar cohomology within fixed genus is the
PBW (Poincar\'e--Birkhoff--Witt) spectral sequence. Filter
$\barB^{(g)}(\cA)$ by \emph{conformal weight}: assign each normally
ordered monomial its total weight (sum of constituent field weights).
The associated graded is the bar complex of a free-field algebra,
reducing to symmetric-function combinatorics.

The $E_1$ page at genus~$g$:
\[
E_1^{p,q}(g)=E_1^{p,q}(g{=}0)\oplus\cE^{p,q}_g,
\]
with the first summand the genus-$0$ bar cohomology determined by
Koszulness of the associated graded and $\cE^{p,q}_g$ the genus-$g$
enrichment from the Hodge bundle, arising from the regular Eisenstein
series coupled to the curvature. \emph{Concentration}:
$E_\infty^{p,q}(g)=0$ for $q\neq 0$ at all $g\ge 1$, for all standard
families. PBW degeneration: the spectral sequence collapses at $E_2$
and bar cohomology concentrates on the diagonal.

The PBW spectral sequence is distinct from the genus spectral sequence
of \S5.5. PBW uses conformal weight within fixed genus to compute bar
cohomology groups; the genus spectral sequence uses the genus
filtration on the deformation algebra to control the MC lift across
genera. One computes \emph{what}; the other determines \emph{whether}.

\subsection*{9.5.\enspace Chiral Hochschild cohomology (Theorem~H)}

The chiral Hochschild complex $\operatorname{ChirHoch}^\bullet(\cA)$
is the derived endomorphism algebra of the identity functor on
$\cA$-modules, computed by the bar construction with bimodule
coefficients. At genus~$0$,
\[
\operatorname{ChirHoch}^\bullet(\cA)\simeq R\Hom_{\cA\text{-bimod}}(\cA,\cA)\simeq\operatorname{Ext}^\bullet_{\cA^e}(\cA,\cA),
\]
where $\cA^e=\cA\otimes\cA^{\mathrm{op}}$ is the enveloping chiral
algebra.

For $\cA=\mathcal W^k(\mathfrak g,f_{\mathrm{prin}})$ a principal
$\mathcal W$-algebra at generic level, the chiral Hochschild cohomology
is concentrated in degrees $\{0,1,2\}$:
\[
\operatorname{ChirHoch}^n(\mathcal W^k(\mathfrak g))=0\text{ for }n>2,\qquad P(t)=1+t^2.
\]
The deformation class in $\operatorname{ChirHoch}^2=\mathbb C$ is the
level deformation $k\mapsto k+\epsilon$. The concentration bound is
the de Rham amplitude on a curve ($\dim X=1$); the continuous
Lie algebra cohomology
$H^*_{\mathrm{cont}}(\operatorname{Lie}(\mathcal W),\operatorname{Lie}(\mathcal W)_0;\mathbb C)=\mathbb C[\Theta_1,\ldots,\Theta_r]$
(Gelfand--Fuchs, $\deg\Theta_i=m_i+1$) is a different, unbounded
invariant. For $\mathfrak g=\mathfrak{sl}_2$ (Virasoro):
$P(t)=1+t^2$. For $\mathfrak g=\mathfrak{sl}_3$ ($\mathcal W_3$):
$P(t)=1+t^2$. Total dimension $2$, never $\mathbb C[\Theta]$.

On the Koszul locus, $\operatorname{ChirHoch}^\bullet(\cA)$ carries an
$E_2$-algebra structure that is formal. The Connes periodicity
operator $S\colon\operatorname{ChirHoch}^n\to\operatorname{ChirHoch}^{n-2}$
intertwines Koszul duality: $S\circ\operatorname{KD}=\operatorname{KD}\circ S$.
At genus~$0$, the chiral Hochschild complex identifies with the bulk
chiral homology complex of Volume~II. The bulk-boundary-line triangle
is the genus-$0$ shadow of this identification:
$\cA_{\mathrm{bulk}}\simeq Z_{\mathrm{der}}(\cB_\partial)\simeq\operatorname{ChirHoch}^\bullet(\cA^!)$.

\medskip\noindent\textbf{Per-family computation.}\enspace
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{llll}
\textbf{Family} & $\ChirHoch^0$ & $\ChirHoch^1$ & $\ChirHoch^2$\\ \hline
$\cH_k$ & $\bC$ & $0$ & $\bC$\\
$V_k(\fg)$ ($k \neq -h^\vee$) & $\bC$ & $\fg$ & $\bC$\\
$\Vir_c$ & $\bC$ & $0$ & $\bC$\\
$\cW_{3,c}$ & $\bC$ & $0$ & $\bC$\\
$\beta\gamma_\lambda$ & $\bC$ & $0$ & $\bC$\\
$V_\Lambda$ & $\bC$ & $0$ & $\bC$
\end{tabular}
\end{center}

\noindent
The Hilbert polynomial is $P(t) = 1 + t^2$ for every family
except affine Kac--Moody, where
$P(t) = 1 + \dim(\fg)\,t + t^2$ (cohomological amplitude
$[0,2]$ in both cases). The degree-$1$ class for $V_k(\fg)$ is
the Lie algebra $\fg$ acting by infinitesimal automorphisms of
the affine algebra; it has total dimension $\dim(\fg) + 2$.
Three invariants that are NOT chiral Hochschild: (i)~the
Gelfand--Fuchs cohomology
$H^*_{\mathrm{cont}}(\mathrm{Lie}(\cA))$ is infinite-dimensional
for Virasoro and $\cW_N$ (polynomial algebra $\bC[\Theta_1, \ldots,
\Theta_r]$ with $\deg \Theta_i = m_i + 1$); (ii)~the naive
centre $Z(\cA) = \{a \in \cA : [a, b] = 0\ \forall b\}$ has
dimension $1$ for $V_k(\fg)$ (the vacuum) but $\ChirHoch^0 = \bC$
matches; (iii)~the categorical Hochschild of the module
category $\HH(\cA\text{-mod})$ carries a Calabi--Yau structure
that differs from the chiral Hochschild by the CY shift.

\subsection*{9.6.\enspace The shadow algebra}

The \emph{shadow algebra} $\cA^{\mathrm{sh}}$ is the cohomology of the
modular cyclic deformation complex as a graded-commutative ring,
\[
\cA^{\mathrm{sh}}:=H_\bullet(\Defcyc^{\mathrm{mod}}(\cA))=\bigoplus_{r\ge 2,g\ge 0}\cA^{\mathrm{sh}}_{r,g}.
\]
The single MC element $\Theta_\cA$ decomposes by degree and genus.
Named shadows are projections:
\[
\kappa(\cA)=\cA^{\mathrm{sh}}_{2,0},\quad\mathfrak C(\cA)=\cA^{\mathrm{sh}}_{3,0},\quad\mathfrak Q(\cA)=\cA^{\mathrm{sh}}_{4,0},\quad\operatorname{Sh}_r(\cA)=\cA^{\mathrm{sh}}_{r,0}\text{ for }r\ge 5.
\]
The shadow algebra organises the entire hierarchy; it is a homotopy
invariant, computed by the Weil homomorphism of the Chern--Weil
dictionary (\S5.4).

The all-degree master equation in the shadow algebra:
$\nabla_H(\operatorname{Sh}_r)+o^{(r)}=0$ for all $r\ge 3$. The
obstruction class $o^{(r)}$ lies in $\cA^{\mathrm{sh}}_{r,0}$ and
measures the failure of $\Theta^{\le r-1}_\cA$ to extend to degree~$r$.

\subsection*{9.7.\enspace BV/BRST identification at genus~$0$}

At genus~$0$, the bar differential of a chiral algebra on $\mathbb C$
is the BRST differential of the associated holomorphic twist,
$(d_{\barB})_{g=0}=Q_{\mathrm{BRST}}$. The bar complex
$\barB^{(0)}_{\mathbb C}(\cA)$ is the BRST complex of the 2d chiral
algebra, and bar-cobar inversion
$\Omega(\barB(\cA))\xrightarrow{\sim}\cA$ (Theorem~B) says the BRST
cohomology processed through the cobar functor reconstructs the
original algebra.

At genus~$1$, the identification acquires curvature:
$d^2_{\mathrm{fib}}=\kappa(\cA)\cdot\omega_1$ is the one-loop anomaly,
and the curved bar complex is the curved BRST complex of the theory
on an elliptic curve. The complementarity
$Q_1(\cA)\oplus Q_1(\cA^!)=H^*(\overline{\cM}_{1,1},\cZ_\cA)$ is the
genus-$1$ anomaly cancellation condition.

At genus $g\ge 2$, the identification with Costello--Gwilliam
requires renormalisation: higher-loop integrals over
$\overline{\cM}_{g,n}$ need regularisation beyond the algebraic
bar-cobar framework, and the correct receptacle is the coderived
category.

For the Heisenberg algebra, the identification is proved at all genera
by four independent paths: zeta-regularisation, Selberg zeta function,
Grothendieck--Riemann--Roch, direct bar computation. The shadow
obstruction tower equals the $L_\infty$-formality obstruction tower
at all degrees.

\medskip
\noindent\textbf{Genus-two shell activation as depth diagnostic.}\enspace
The genus-two shell profile independently confirms the depth
classification:

\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lccc}
& $\Theta^{(2)}_{\mathrm{loop}^2}$ & $\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}$ & $\Theta^{(2)}_{\mathrm{pf}}$\\
\hline
\textbf{G} (Heisenberg, lattice) & $\checkmark$ & --- & ---\\
\textbf{L} (affine $\widehat{\mathfrak g}_k$) & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\textbf{C} ($\beta\gamma$) & $\checkmark$ & --- & ---\\
\textbf{M} (Virasoro, $\mathcal W_N$) & $\checkmark$ & $\checkmark$ & $\checkmark$
\end{tabular}
\end{center}

\noindent
G and C activate only the loop$\circ$loop shell; L and M activate all
three including planted-forest. The diagnostic distinguishing L from M
is the critical discriminant $\Delta=8\kappa S_4$: zero for L
($S_4=0$), nonzero for M.

\medskip
\noindent\textbf{Structural refinements.}\enspace
The three bar complexes on a chiral algebra (ordered tensor $T^c$,
symmetric $\operatorname{Sym}^c$, Chevalley--Eilenberg
$\operatorname{Lie}^c$) sit in a chain
$\operatorname{Lie}^c\hookrightarrow\operatorname{Sym}^c\hookrightarrow T^c$
with distinct coalgebra structures at each level
(Theorem~\ref{thm:three-bar-complexes}). The averaging map
$\mathrm{av}\colon T^c\to\operatorname{Sym}^c$ from ordered to
symmetric is surjective but not split: the kernel at degree~$3$
contains the Drinfeld associator $\Phi_{\mathrm{KZ}}(\cA)$, and the
fibre of splittings is a torsor for $\mathrm{GRT}_1$. The $E_1$
ordered bar complex is therefore the natural primitive object; the
modular/symmetric story is its $\Sigma_n$-coinvariant image
(Theorem~\ref{thm:e1-primacy}). The genus-$3$ cross-channel
correction for $\mathcal W_3$ has been computed by summing over all
$42$ stable graphs of $\overline{\cM}_{3,0}$
(Proposition~\ref{prop:w3-genus3-cross-channel}): the cross-channel
tower accelerates with genus and dominates the scalar part
$\kappa\cdot\lambda_g^{\mathrm{FP}}$ by genus~$4$
\textsc{(all-weight, with cross-channel correction)}.

On the open/closed side, the Koszul dual cooperad
$\mathsf{SC}^{\mathrm{ch,top},!}$ decomposes into three sectors:
closed ($\dim=(n-1)!$, Lie cooperad), open ($\dim=m!$, Ass cooperad),
and mixed ($\dim=(k-1)!\binom{k+m}{m}$). The mixed sector
encodes the bulk-to-boundary module structure by which the chiral
derived centre acts on the boundary algebra.

The BV/BRST${}={}$bar identification at higher genus
(Conjecture~\ref{conj:master-bv-brst}): the chain-level obstruction
(harmonic propagator correction) is resolved for classes G, L, and C,
for G and L by the Heisenberg sewing theorem and its extension to
affine algebras, for C by contact decoupling. For class M (Virasoro,
$\mathcal W_N$) the identification holds on bar cohomology but fails
at the chain level: the harmonic propagator produces a nonvanishing
quartic obstruction, so a coderived reformulation is needed.

\subsection*{9.8.\enspace The 14-characterisation circuit}

The ten unconditional equivalences (i)--(x), the Lagrangian criterion
(xi), the $\cD$-module purity implication (xii), and the six
additional characterisations (a)--(f) organise into a circuit with
four hubs:

\begin{center}
\small
\begin{tabular}{ll}
\textbf{Hub} & \textbf{Characterisations}\\ \hline
Homological & (i) Koszulness, (ii) PBW collapse,
(iv) Ext diagonal, (ix) Kac--Shapovalov\\
Homotopical & (iii) $A_\infty$ formality,
(v) bar-cobar qi, (vi) Barr--Beck--Lurie, (b) $E_2$-formality\\
Geometric & (vii) FH concentration, (x) FM acyclicity,
(xi) Lagrangian, (xii) $\cD$-module purity\\
Tropical & (e) tropical Koszulness, (c) curve independence,
(d) PBW universality\\
\end{tabular}
\end{center}

\noindent
The core chain
(i)$\Leftrightarrow$(ii)$\Leftrightarrow$(iii)$\Leftrightarrow$%
(v)$\Leftrightarrow$(viii) forms a pentagon connecting all four
hubs. Each link is an independent theorem:
\begin{itemize}[nosep]
\item (i)$\Leftrightarrow$(ii): PBW concentration controls
bar resolution by conformal-weight filtration.
\item (ii)$\Leftrightarrow$(iii): HPL transfer converts spectral
collapse to $A_\infty$ formality (Keller classicality theorem).
\item (iii)$\Leftrightarrow$(v): $A_\infty$ formality on
$H^*(\barB)$ is equivalent to the counit
$\Omega(\barB(\cA)) \to \cA$ being a qi (a chain-level
inversion, not merely a cohomological isomorphism).
\item (v)$\Leftrightarrow$(viii): bar-cobar inversion gives
$\ChirHoch^*(\cA) \simeq R\Hom_{\cA^e}(\cA,\cA) \simeq
H^*(B(\cA))$; the computation in the bar model yields
concentration in degrees $\{0,1,2\}$.
\end{itemize}
From this core: (iv) by the Ext spectral sequence from (ii);
(vi) by conservativity of the $\barB \dashv \Omega$ adjunction
with log-FM totalisation; (vii) by the identification
$\barB = \int_X$ (the bar complex computes factorisation
homology on $X$); (ix) by non-degeneracy of the
Kac--Shapovalov form forcing PBW injectivity at the relevant
conformal weights; (x) by the FM stratum restriction carrying
PBW concentration stratum-by-stratum.

\medskip\noindent\textbf{The Lagrangian criterion (xi).}\enspace
Under perfectness and nondegeneracy of the ambient tangent
complex, $\cM_\cA$ and $\cM_{\cA^!}$ are Lagrangians in a
$(-1)$-shifted symplectic stack $\cM_{\mathrm{comp}}$. Their
transversality is the geometric incarnation of bar-cobar
inversion: the Lagrangian intersection
$\cM_\cA \cap \cM_{\cA^!}$ is clean iff $\cA$ is Koszul. The
proof uses the PTVV derived intersection theory, specifically
the $(-1)$-shifted symplectic structure on the mapping stack
$\mathrm{Map}(X, \cM_{\mathrm{comp}})$ for smooth proper~$X$.
Perfectness ensures the cotangent complex is perfect (bounded
coherent), which is automatic for all standard landscape
families but not for arbitrary chiral algebras.

\medskip\noindent\textbf{The $\cD$-module purity direction
(xii)$\Rightarrow$(x).}\enspace
Each $\barB_n(\cA)$ on $\FM_n(X)$ is a $\cD$-module. If it is
pure of weight $n$ as a mixed Hodge module (meaning the weight
filtration has a single nonzero graded piece at weight $n$), then
its restriction to any FM boundary stratum is acyclic outside
degree $0$, which is characterisation (x). The forward direction
uses the weight filtration on nearby cycles; the converse
(concentration $\Rightarrow$ purity) would require concentration to
\emph{force} purity, which is not known in general.

\subsection*{9.9.\enspace Scalar saturation: the proof}

The scalar saturation theorem asserts that for a one-parameter
algebraic family $\cA_k$, the universal MC element
$\Theta_{\cA_k}$ is determined by the single scalar
$\kappa(\cA_k)$. The proof has three steps:

\medskip\noindent\textbf{Step~1} (Whitehead reduction at generic
level). The cyclic deformation complex $\Defcyc(\cA_k)$ at
generic $k$ has a primitive filtration with associated graded
controlled by Lie algebra cohomology. The relevant group is
$H^2(\fg; \Sym^q V)$ for the Lie algebra $\fg$ underlying the
chiral algebra at the generic point. For reductive $\fg$ and
generic $k$, the Whitehead lemma gives $H^2(\fg; M) = 0$ for
any finite-dimensional $\fg$-module $M$; in particular
$H^2(\fg; \Sym^q V) = 0$ for all $q$. The vanishing at
$q = 0$ kills the primitive degree-$2$ obstruction; the
vanishing at all $q$ kills all higher corrections to the
degree-$2$ MC class. The unique lift is $\kappa(\cA_k) \cdot
\eta_{\mathrm{univ}} \otimes \Lambda_{\mathrm{univ}}$.

\medskip\noindent\textbf{Step~2} (semicontinuity). The
non-vanishing locus
$E = \{k \in \bC : H^2_{\mathrm{cyc,prim}}(\cA_k) \neq 0\}$
is Zariski-closed by upper semicontinuity of cohomology
dimensions in algebraic families. Since the generic point (which
is the Heisenberg limit $k \to \infty$) has
$H^2_{\mathrm{cyc,prim}} = 0$, the set $E$ is a proper
Zariski-closed subset of $\bC$, hence finite. If $E$ is
empty, scalar saturation holds at all levels; if $E$ is
nonempty, it consists of finitely many exceptional levels.

\medskip\noindent\textbf{Step~3} (explicit verification).
For $\fg = \mathfrak{sl}_N$ with $N = 2, \ldots, 10$, the
computation verifies $E = \varnothing$: no exceptional level
exists. The computation uses the PBW spectral sequence at each
candidate level (roots of the Kac--Shapovalov determinant,
admissible levels, critical level) and confirms that
$H^2_{\mathrm{cyc,prim}} = 0$ everywhere. The critical level
$k = -h^\vee$ is included: $\kappa(-h^\vee) = 0$, so scalar
saturation gives $\Theta = 0$, consistent with the
Feigin--Frenkel centre (the MC element vanishes when the
curvature vanishes).

\subsection*{9.10.\enspace The admissible-level question}

At admissible levels $k = -h^\vee + p/q$ ($p \ge h^\vee$,
$q \ge 1$, $\gcd(p,q) = 1$), the universal vertex algebra
$V_k(\fg)$ is \emph{not} simple: the maximal ideal $J_k$
produces the simple quotient $L_k(\fg) = V_k(\fg)/J_k$. The
bar-Koszul theory bifurcates:
\begin{enumerate}[label=(\roman*),nosep]
\item $V_k(\fg)$ (the universal algebra) is chirally Koszul
at every level, including admissible and critical, by PBW
universality: it is freely strongly generated by the
currents $J^a$, and PBW universality applies.
\item $L_k(\fg)$ (the simple quotient) at admissible levels
is a different question. The quotient map
$V_k(\fg) \twoheadrightarrow L_k(\fg)$ kills singular vectors,
potentially destroying the PBW property.
\end{enumerate}

The rank-$1$ case is completely settled: $L_k(\mathfrak{sl}_2)$
is chirally Koszul at all admissible levels $k = -2 + p/q$,
because the bar complex of the simple quotient inherits
concentration from the universal algebra via the surjection
$\barB(V_k) \twoheadrightarrow \barB(L_k)$ (the bar functor
preserves surjections).

At rank $\ge 2$ with denominator $q \ge 3$, Koszulness of
$L_k(\fg)$ is expected to fail: the abelian Cartan subalgebra
$\fh \subset \fg$ produces a $\mathrm{rk}(\fg)$-dimensional bar
obstruction in $H^2(\barB(L_k))$ that does not arise for $V_k$.
The obstruction comes from the interaction between singular
vectors and the Cartan direction, which is invisible at rank $1$.
This constitutes a rank-dependent Koszulness failure that
distinguishes universal from simple vertex algebras at
admissible levels. The precise rank threshold and the structure of
the obstruction complex are the subject of an ongoing programme.

The practical consequence: all formulas in this survey apply to
\emph{universal} vertex algebras $V_k(\fg)$ at all levels without
restriction. Specialisation to simple quotients $L_k(\fg)$
requires additional analysis that depends on the level denominator
and the rank of $\fg$.

% ====================================================================
% TRACK B: sections 10--13 (open/closed, PVA quantization, holography,
% completion and frontier)
% ====================================================================

\section*{10.\quad The open/closed world (Volume II)}
% ====================================================================

Sections~1--9 construct $E_n$-chiral algebras as
algebraic-geometric objects on curves: bar complexes on every
curve geometry, $R$-matrices, Yangian structures, derived chiral
centres carrying $E_2$/$E_3$ structure, and the
$\SCchtop$ datum on the pair
$(\cZ^{\der}_{\ch}(\cA),\, \cA)$. Volume~II discovers that
these constructions are physics: the derived chiral centre IS the
bulk algebra of a real 3d holomorphic-topological gauge theory.
The passage from algebraic geometry to physics is through the
derived centre.

On the product $\bC_z \times \bR_t$, the holomorphic direction
produces the bar differential of Sections~1--9, extracting OPE
residues from collisions in the holomorphic plane. The
topological direction produces the deconcatenation coproduct,
splitting an ordered tensor sequence at a cut point of the real
line. The two are unified by the \emph{holomorphic-topological
Swiss-cheese operad} $\SCchtop$: closed colour
$\mathrm{ch} = \FM_k(\bC)$ governs holomorphic factorization,
open colour $\mathrm{top} = E_1(m)$ governs topological
factorization, and the open/closed mixed sector encodes the
action of bulk on boundary.

The primitive object of 3d HT quantum field theory on
$\bC_z \times \bR_t$ is not the bar complex but the open/closed
factorization dg-category $\cC$ on the bordified curve
$\widetilde X_D$. Objects are boundary conditions, morphisms
are open-string states, and a vacuum $b$ produces a boundary
algebra $A_b = \End_\cC(b)$ only up to Morita equivalence. The
governing operad is $\SCchtop$; it is homotopy-Koszul (proved
via Kontsevich formality), so the bar-cobar adjunction on
$\SCchtop$-algebras is a Quillen equivalence.

The bar complex of Volume~I is the ordered $E_1$ coalgebraic
engine for $\cC$: its differential records holomorphic
collision data, and its coproduct records ordered topological
splitting. The $\SCchtop$ structure itself lives on the
derived-center pair
$(C^\bullet_{\mathrm{ch}}(A_b, A_b),\, A_b)$.
Three objects must never be conflated:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item the \emph{bar complex} $\barB(A_b)$ classifies twisting
morphisms, universal couplings between $A_b$ and $A_b^!$;
\item the \emph{chiral derived centre}
$\cZ^{\der}_{\ch}(\cC) =
R\Hom_{\Fun(\cC,\cC)}(\Id, \Id)$ is the universal bulk,
computed by chiral Hochschild cochains in any chart;
\item the Koszul dual $A_b^!$ governs the line-operator
category $A_b^!\text{-mod}$.
\end{enumerate}
The primitive hierarchy
\[
\cC_{\op}
\;\xrightarrow{\End(b)}\;
A_b
\;\xrightarrow{\barB}\;
\barB(A_b)
\;\xrightarrow{\Theta}\;
\Theta_\cA
\;\xrightarrow{+\mu^{M_j}}\;
\Theta^{\oc}_\cA
\]
records successive lossy functors: $\cC_{\op}$ is Morita
invariant; $A_b$ depends on $b$; $\barB$ forgets the bulk;
$\Theta_\cA$ is the closed-sector MC element;
$\Theta^{\oc}_\cA$ restores open/closed data. Modularity is
determined by the open sector: a cyclic trace on $\End(b)$
seeds the Calabi--Yau structure, the annulus identification
$\int_{S^1} \cC \simeq \HH_\bullet(\cC)$ is the first modular
shadow, and clutching along boundary circles raises genus.

Volume II proceeds in four stages. Stage~1 (local one-colour
theorem: Swiss-cheese universality of the derived centre),
Stage~2 (open primitive: $\cC$ with Morita invariance), and
Stage~3 (globalisation on tangential log curves $(X, D, \tau)$)
are proved (Stage~3 locally; global extension modest). In Stage~4 (modularisation), the open/closed MC
element $\Theta^{\oc}_\cA$ is constructed, the modular MC
equation holds at all genera, and the projection principle
recovers both the closed-sector genus tower and the
open-sector module structures. The annulus trace is proved;
the independent higher-genus derivation and chain-level
cooperad compatibilities remain open.

\subsection*{10.1.\enspace The Swiss-cheese operad
$\SCchtop$}

Two colours $\{\mathrm{ch}, \mathrm{top}\}$, with operation
spaces
\begin{align*}
\SC(\mathrm{ch}^k; \mathrm{ch}) &= \FM_k(\bC),\\
\SC(\mathrm{ch}^k, \mathrm{top}^m; \mathrm{top})
&= \FM_k(\bC) \times E_1(m),\\
\SC(\ldots, \mathrm{top}, \ldots; \mathrm{ch}) &= \varnothing.
\end{align*}
Closed-to-closed is the Fulton--MacPherson compactification in
$\bC$; the mixed direction combines holomorphic configurations
acting on the fibre above a topological interval; open-to-closed
is forbidden. Operadic composition is the boundary stratification
of FM spaces in the holomorphic direction and nested interval
inclusion in the topological direction.

A bar element of tensor degree $k$ lives on the product
$\FM_k(\bC) \times \Conf_k(\bR)$. The bar differential extracts
OPE residues along collision divisors of the first factor: when
points $z_i$, $z_j$ collide, the residue of
$\eta_{ij} = d\log(z_i - z_j)$ yields the mode $a_{(n)}b$. The
coproduct splits the ordered sequence at a cut point of the
second factor: for $t_1 < \cdots < t_k$ with $t_p < c < t_{p+1}$,
$(a_1\otimes\cdots\otimes a_k)$ decomposes as
$(a_1\otimes\cdots\otimes a_p)\otimes(a_{p+1}\otimes\cdots\otimes a_k)$.
The bar complex with both structures is a
$\SCchtop$-algebra.

\subsection*{10.2.\enspace Homotopy-Koszulity}

The classical Swiss-cheese operad $\SC$ is Koszul
(Livernet--Voronov, Ginzburg--Kapranov), with quadratic
presentation and distributive-lattice criterion on the poset
of nested disks. Kontsevich formality supplies a quasi-iso
$\Phi\colon \SCchtop \xrightarrow{\sim} \SC$ from
configuration-space integrals on FM spaces with propagators,
extended by including $\mathbb H$ and $\bR$. The bar-cobar
adjunction preserves quasi-isos, and two-out-of-three in the
operadic model category gives
$\Omega\mathbf B(\SCchtop) \xrightarrow{\sim} \SCchtop$. The
bar-cobar adjunction on $\SCchtop$-algebras is therefore a
Quillen equivalence, with three consequences:
\begin{enumerate}[label=(\roman*),nosep]
\item every $\SCchtop$-algebra admits a cofibrant bar-cobar
resolution;
\item the homotopy category of $\SCchtop$-algebras is
equivalent to that of coalgebras over the Koszul dual
cooperad;
\item the line-operator category $A_b^!\text{-mod}$ is
unconditionally defined without finiteness hypotheses on $\cA$.
\end{enumerate}

\subsection*{10.3.\enspace The $A_\infty$ chiral algebra structure}

The full Swiss-cheese MC element $\alpha_T \in \MC(\fg^{\SC}_T)$
lives in the convolution algebra
$\fg^{\SC}_T = \Hom_\Sigma(\mathbf B(\SCchtop),
\End_{(B_\partial, \cC_{\mathrm{line}})})$. Its closed-colour
projection $(m_k)_{k \ge 1}$ encodes the $A_\infty$ chiral
algebra on $\cA$. Each $m_k\colon \cA^{\otimes k} \to
\cA(\!(\lambda_1)\!)\cdots(\!(\lambda_{k-1})\!)$ is a
configuration-space integral on
$\FM_k(\bC) \times \Conf_k(\bR)$, with the holomorphic factor
producing OPE singularities and the topological factor
producing the ordering. Summing over trees $T$ with $k$ leaves,
$m_T(a_1,\ldots,a_k) = \int_{\FM_k(\bC)}\omega_T \prod_{v}
a_{(n_v)} b_v$. The Maurer--Cartan equation is the spectral
Stasheff identity: Stokes' theorem on boundary strata of
$\FM_k(\bC)$ produces the $A_\infty$ relations.

\subsection*{10.4.\enspace PVA descent (Theorem G)}

On cohomology, the operations simplify. The regular part of
$m_2$ is a commutative associative product
$\mu(a,b) = \Reg_{z_1 \to z_2} m_2(a(z_1), b(z_2))$;
commutativity follows from the $\bZ/2$ involution of
$\FM_2(\bC)$, associativity from the three FM$_3$ boundary
strata. The singular part defines the lambda-bracket
$\{a_\lambda b\} = \Res_{z_1 \to z_2} e^{\lambda(z_1 - z_2)}
m_2(a(z_1), b(z_2))$; the exponential extracts all pole orders.
All $m_{k \ge 3} = 0$ on cohomology because $\Conf_k(\bR)$ is
contractible for $k \ge 3$.

The Arnold relation
$\eta_{12}\wedge\eta_{23} + \eta_{23}\wedge\eta_{31}
+ \eta_{31}\wedge\eta_{12} = 0$ on $\FM_3(\bC)$ is equivalent
to the three codim-1 boundary divisors of $\overline M_{0,4}$
summing to zero in homology; its residue against
$a\otimes b\otimes c$ produces the Jacobi identity for
$\{-_\lambda -\}$. The three-face Stokes identity applied to
$\omega = \eta_{12}\wedge\eta_{23}\cdot a(z_1)b(z_2)c(z_3)$
produces the Leibniz rule $\{a_\lambda(b\cdot c)\} =
\{a_\lambda b\}c + b\{a_\lambda c\}$. The exchange cylinder
on $\FM_2(\bC)\times E_1(2)$ gives skew-symmetry
$\{a_\lambda b\} = -\{b_{-\lambda - \partial} a\}$. Thus
$(\mu, \{-_\lambda -\})$ is a $(-1)$-shifted Poisson vertex
algebra, each axiom in one line from the geometry of FM.

(Vol~I convention: we state the PVA in OPE modes; Vol~II uses
lambda-brackets throughout, and the two conventions are
translated by the standard
$\{a_\lambda b\} = \sum_{n \ge 0}\lambda^n a_{(n)}b/n!$.)

\subsection*{10.5.\enspace The Heisenberg algebra in Swiss-cheese coordinates}

For $\cH_k$: $m_2(J, J) = k \cdot \mathbf 1$,
$m_{k \ge 3} = 0$, $\{J_\lambda J\} = k\lambda$. All higher
operations vanish because the OPE has no simple pole. The
spectral $R$-matrix is the scalar $R(z) = \exp(k/z)$; YBE
holds trivially. The PVA is the free bosonic PVA, the
universal enveloping PVA of the rank-one abelian Lie conformal
algebra.

\subsection*{10.6.\enspace The Koszul triangle}

From $\cC$ on $\widetilde X_D$ three independent objects arise:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item Boundary $A_b = \End_\cC(b)$: a chart.
\item Bulk $\cZ^{\der}_{\ch}(\cC) =
R\Hom_{\Fun(\cC,\cC)}(\Id, \Id)$: the universal bulk, Morita
invariant, computed by chiral Hochschild cochains.
\item Lines
$A_b^!{}_\infty = D_{\Ran}(\barB(A_b))$: the homotopy Koszul
dual, whose cohomology on the Koszul locus recovers the strict
dual $A_b^! = (H^*(\barB(A_b)))^\vee$. The module category
$A_b^!\text{-mod}$ with spectral braiding $R(z)$ is the
braided tensor category of line operators.
\end{enumerate}
The triangle of identifications
\[
\cZ^{\der}_{\ch}(\cC)
\;\simeq\;
\HH^\bullet(A_b)
\;\simeq\;
\mathrm{ChirHoch}^\bullet(A_b^!),
\qquad
A_b^!\text{-mod} = \{\text{line operators}\}
\]
relates three distinct functors: endomorphisms (bulk),
Ran-space Verdier duality (lines), and identity-bimodule
endomorphisms (centre). The bar complex classifies twisting
morphisms, not the bulk.

\medskip\noindent\emph{Spectral braiding.} Stokes' theorem on
$\FM_3(\bC)$ applied to $\alpha\star\alpha\star\alpha$ decomposes
the boundary into three pairwise collision divisors, one for
each side of the Yang--Baxter equation
$R_{12}R_{13}R_{23} = R_{23}R_{13}R_{12}$.

\medskip\noindent\emph{Bulk $=$ derived centre.} Let
$\cB_\partial$ be the boundary factorization algebra on $\bR$.
Its derived centre
$Z_{\der}(\cB_\partial) = R\Hom_{\cB_\partial\text{-bimod}}
(\cB_\partial, \cB_\partial)$
computes endomorphisms of the identity bimodule. The
$E_1$-structure gives
$Z_{\der}(\cB_\partial) \simeq \HH^\bullet(\cB_\partial)$ as
$E_2$-algebra. The Swiss-cheese structure identifies the
holomorphic bulk with this $E_2$-algebra.

\medskip\noindent\emph{From $E_2$ to $E_3$: the topologisation
mechanism.}\enspace
The $E_2$-algebra structure on the derived centre is the
minimal output. When $\cA$ carries a conformal vector $T(z)$
at non-critical level, the Sugawara construction
$T(z) = \{Q, G(z)\}$ makes $\bC$-translations $Q$-exact:
$L_{-1} = [Q, G_0]$ on the BRST complex. In cohomology, the
complex structure on $\bC$ becomes irrelevant: the $E_2$
holomorphic structure degenerates to an $E_2$ topological
structure, and Dunn additivity
$E_1^{\mathrm{top}} \otimes E_2^{\mathrm{top}}
\simeq E_3^{\mathrm{top}}$ promotes the combined structure
to $E_3$-topological; the conformal vector kills the chiral
direction. For affine Kac--Moody
$V_k(\fg)$ at non-critical level $k \neq -h^\vee$: proved
cohomologically and chain-level on a qi-equivalent model.
For general chiral algebras with conformal vector: conjectural
(the 3d HT BRST complex is conditional). For algebras without
conformal vector (Heisenberg at critical level, lattice VOAs
without Sugawara): stuck at $\SCchtop$.

The $E_3$ identification theorem: for simple $\fg$ at
non-critical level, the derived chiral centre
$\cZ^{\der}_{\ch}(V_k(\fg))$ is identified as an
$E_3$-topological algebra that forms a family over
$\hbar \cdot H^3(\fg)[[\hbar]]$. The identification uses
$E_3$ formality (Kontsevich) and the one-dimensionality of
$H^3(\fg)$ for simple $\fg$ to force order-by-order
uniqueness. For non-simple $\fg$: $H^3(\fg)$ may be
higher-dimensional, and the identification is open.

\medskip\noindent\emph{The Koszul dual cooperad.}\enspace
The homotopy-Koszul dual cooperad
$\mathsf{SC}^{\mathrm{ch,top},!} = (\mathrm{Lie}^c, \mathrm{Ass}^c,
\text{shuffle-mixed})$ has:
\begin{itemize}[nosep]
\item Closed sector: $\dim \mathsf{SC}^{\mathrm{ch,top},!}(\mathrm{cl}^n; \mathrm{cl})
= (n-1)!$ (Lie cooperad). The factorial growth
distinguishes it from $\SCchtop$ itself, which has
$\dim \SCchtop(\mathrm{cl}^n; \mathrm{cl}) = 1$ (commutative).
\item Open sector: $\dim \mathsf{SC}^{\mathrm{ch,top},!}(\mathrm{op}^m; \mathrm{op})
= m!$ (associative cooperad, self-dual).
\item Mixed sector:
$\dim \mathsf{SC}^{\mathrm{ch,top},!}(\mathrm{cl}^k, \mathrm{op}^m; \mathrm{op})
= (k-1)!\binom{k+m}{m}$, encoding shuffle-mixed compositions.
\end{itemize}
$\SCchtop$ is NOT Koszul self-dual: the closed dimensions are
$(n-1)! \neq 1$. What IS true: the bar-cobar duality
functor is an involution $((P^!)^! \simeq P$ for Koszul
operads), but the operad $P = \SCchtop$ is not isomorphic to
$P^!$. The Koszul duality exchanges $\Com$ (closed) with
$\mathrm{Lie}$ (closed); $\Ass$ (open) is self-dual.

\subsection*{10.7.\enspace Curved Swiss-cheese at $g \ge 1$}

At genus $g \ge 1$, the bar complex carries curvature:
\[
d_{\mathrm{fib}}^2 \;=\; \kappa(\cA)\cdot\omega_g,
\]
with $\omega_g$ the Arakelov $(1,1)$-form representing the first
Chern class of the relative dualising sheaf. The coproduct
remains strictly coassociative: the interval $\bR$ has no
topology, so the curvature lives entirely in the holomorphic
direction. The total corrected differential
$D_g = d_{\mathrm{fib}} + \nabla^{\GM}_g$ restores flatness by
coupling the ordering to the Hodge bundle:
$d_{\mathrm{fib}}^2 + [d_{\mathrm{fib}}, \nabla^{\GM}]
+ (\nabla^{\GM})^2 = \kappa\omega_g - \kappa\omega_g = 0$.

The derived category must be replaced by the coderived category
$\mathsf D^{\co}(\cA^{(g)})$: ordinary $d^2 = 0$ fails at $g \ge
1$, every object is acyclic in the derived sense, and the
correct homotopy theory comes from totalising the curvature
bicomplex. Passage from derived to coderived is the categorified
form of passage from $d^2 = 0$ to curved MC
$d\alpha + \alpha^2 + \kappa\omega = 0$.

\subsection*{10.8.\enspace Lagrangian self-intersection}

Volume~II identifies the geometric substrate of the bar
construction: the bar complex is the structure sheaf of the
Lagrangian self-intersection
$\mathfrak S = \cL \times_\cM \cL$ in a $(-2)$-shifted
symplectic stack. Every theorem is a face of that geometry:
Theorem~A is the groupoid comodule-module adjunction for
$\mathfrak S$; Theorem~B (bar-cobar inversion) reconstructs
the Lagrangian from its clean self-intersection; Theorem~C
(complementarity) is two Lagrangians whose intersection
carries a $(-1)$-shifted symplectic structure; Theorem~D is
the Kodaira--Spencer class; Theorem~H (chiral Hochschild polynomial
growth) is the HKR theorem for the Lagrangian embedding.

\subsection*{10.9.\enspace Factorization-primary hierarchy}

$\SCchtop$ is a \emph{local model}: the formal completion of a
factorisation structure at collision points. The global truth
is a factorisable $\cD$-module on $\Ran(\Sigma_g)$ over
$\overline\cM_g$. Six layers:
\begin{enumerate}[label=(\roman*),nosep]
\item Geometric substrate: smooth and stable nodal curves,
$\Ran$ space, $\overline\cM_{g,n}$.
\item Factorizable $\cD$-modules (Beilinson--Drinfeld).
\item HT product geometry $\Sigma_g \times \bR$.
\item Bar as factorization coalgebra on $\Ran(X)$.
\item Koszul duality as factorization duality; Feynman
involutivity $\mathrm{FT}^2 \simeq \id$.
\item Three models as three gauges: flat associated graded
($D_0^2 = 0$, operadic/local), corrected holomorphic
($D^{(g)2} = 0$, Fay trisecant, still local), curved geometric
($d_{\mathrm{fib}}^2 = \kappa\cdot\omega_g$, Arakelov, global).
\end{enumerate}
The curvature measures what the local extraction loses: it is
the monodromy of the $\cD$-module connection around $B$-cycles
of $\Sigma_g$. The modular bar complex $\barB_{\mod}(\cA)$ is
flat because it couples all genera simultaneously via $D_1$;
the genus-fixed bar complex is curved because restriction
decouples this connection.

The relative Feynman transform
$\mathrm{FT}_{\mathsf{Com}_{\mod}/\SCchtop}$ mediates between
factorisation (global) and operadic (local) viewpoints. The
modular bar coalgebra is an algebra over this transform;
homotopy-involutivity plus factorisation Koszul duality gives
the flat-derived / curved-coderived comparison at all genera.

\medskip\noindent\textbf{Three models compared.}\enspace
The three models of the bar complex correspond to three levels
of geometric approximation:
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{llll}
\textbf{Model} & \textbf{Differential} & \textbf{Domain}
 & \textbf{Status}\\ \hline
Flat (operadic) & $D_0^2 = 0$ & formal disk
 & proved, all families\\
Corrected (holomorphic) & $D^{(g)2} = 0$ & smooth curve
 & proved, uses Fay trisecant\\
Curved (geometric) & $d_{\fib}^2 = \kappa\omega_g$ & Arakelov
 & proved, coderived category
\end{tabular}
\end{center}
\noindent
The flat model is the operadic bar complex on a formal disk; it
sees only the OPE data and produces $D_0^2 = 0$ by Arnold plus
Borcherds. The corrected model on a smooth curve restores the
$A$-cycle periods by the Fay trisecant identity; the $B$-cycle
periods produce quasi-periodicity factors that the corrected model
absorbs by the KZB connection. The curved model on a stable curve
over $\overline\cM_g$ has $d_{\fib}^2 = \kappa\omega_g$; the
curvature is the Chern class of the Hodge bundle, and flatness is
restored by the Gauss--Manin connection across moduli. The three
models are related by restriction: curved $\to$ corrected
(restricting to a smooth fiber) $\to$ flat (restricting to a
formal neighborhood of a point).

\subsection*{10.10.\enspace Four-stage architecture}

\emph{Stage~1.} $\SCchtop$ homotopy-Koszul; bar-cobar is
Quillen-equivalent; chiral derived centre
$\simeq C^\bullet_{\ch}(A_b, A_b)$ is the universal bulk.
\textsc{Proved.}

\emph{Stage~2.} Primitive object is the open factorisation
dg-category $\cC$; $A_b$ is a chart; bulk is Morita invariant.
\textsc{Proved.}

\emph{Stage~3.} Tangential log curves $(X, D, \tau)$ provide
bordered FM compactification; local-global bridge lifts
operadic structure to factorisable $\cD$-module on $\Ran(X)$.
\textsc{Proved locally; modest globally.}

\emph{Stage~4.} Trace and clutching on the open sector produce
the full open/closed MC element $\Theta^{\oc}$. Annulus trace
is proved; full chain-level clutching is programme.

Five negative principles: (N1) bar $\neq$ bulk; (N2) boundary
algebra is a chart; (N3) tangential log geometry required;
(N4) modularity is trace plus clutching on the open sector;
(N5) dg-shifted Yangian is proved for affine lineage only,
extension to non-standard families is programme.

\medskip\noindent\textbf{Stage~1 in detail: the local one-colour
theorem.}\enspace
The chiral derived centre
$\cZ^{\der}_{\ch}(\cA) = C^\bullet_{\ch}(\cA, \cA)$ is computed
by chiral Hochschild cochains: the cochain complex
$\prod_{k \ge 0} \Hom(\cA^{\otimes k}, \cA)$ with differential
from the bar resolution. On the Koszul locus, the complex
concentrates in cohomological degrees $\{0, 1, 2\}$ by
Theorem~H; the chiral Gerstenhaber bracket
$[-,-]_G \colon C^p \otimes C^q \to C^{p+q-1}$ makes
$C^\bullet_{\ch}(\cA, \cA)$ into an $E_2$-algebra. The
$\SCchtop$ structure emerges: the pair
$(C^\bullet_{\ch}(\cA, \cA),\, \cA)$ carries an
$\SCchtop$-algebra structure where the closed colour acts on
$\cA$ (bulk acts on boundary) and the open-to-closed map is
zero (boundary does not produce bulk).

The passage from $E_2$ to $E_3$ requires a conformal vector:
the Sugawara construction $T(z) = \{Q, G(z)\}$ makes
$\bC$-translations $Q$-exact, killing the holomorphic direction
in cohomology. For affine Kac--Moody $V_k(\fg)$ at non-critical
level $k \neq -h^\vee$: the Sugawara $T$ is explicit, the
topologisation is proved (cohomologically, and chain-level
on a qi-equivalent model), and the $E_3$-topological structure on
$\cZ^{\der}_{\ch}(V_k(\fg))$ is identified as a family over
$\hbar \cdot H^3(\fg)[[\hbar]]$. For Virasoro and $\cW$-algebras
with conformal vector: conjectural (the 3d HT BRST complex is
conditional). Without conformal vector (Heisenberg at $k = 0$,
critical level, lattice VOAs without Sugawara): stuck at
$\SCchtop$. The Swiss-cheese structure is the generic case;
$E_3$-topological is special.

\medskip\noindent\textbf{Stage~2 in detail: Morita invariance.}\enspace
The primitive object $\cC$ is a dg-category on the bordified
curve $\widetilde X_D$. Morita equivalence is the statement
that $\cZ^{\der}_{\ch}(\cC) \simeq
\cZ^{\der}_{\ch}(\cC')$ whenever $\cC$ and $\cC'$ are derived
Morita equivalent. The boundary algebra $A_b = \End_\cC(b)$
depends on the choice of boundary condition $b$; the bulk does
not. Two boundary conditions $b, b'$ produce Morita equivalent
boundary algebras iff the bimodule
${}_b\cC_{b'} = \Hom_\cC(b, b')$ is an invertible bimodule.
The holographic datum $\cH(T)$ is therefore boundary-dependent:
the $R$-matrix, the Koszul dual, and the line-operator category
all depend on the choice of $b$.

\medskip\noindent\textbf{Stage~3 in detail: tangential log
globalisation.}\enspace
A tangential log curve $(X, D, \tau)$ consists of a smooth curve
$X$, a reduced effective divisor $D \subset X$
(the marked points), and a tangential base point
$\tau \in T_D X / \bC^*$ at each component of $D$ (a ray in the
tangent space, specifying the ordering direction). The
log-FM compactification $\FM^{\log}_n(X, D)$ extends $\FM_n(X)$
by allowing points to collide with boundary divisors; the
log-differential forms $\Omega^*_{\log}(\FM^{\log}_n)$ carry both
holomorphic and tangential data.

The local-global bridge: operadic $\SCchtop$ data at each point
of $D$ assemble into a factorisable $\cD$-module on
$\Ran(X \setminus D)$ via the Beilinson--Drinfeld factorisation
construction. The modular extension couples the factorisable
data to $\overline\cM_{g,n}$ via the universal curve.

\subsection*{10.11.\enspace The 3d MC colour decomposition}

The 3d MC element $\Theta^{\oc}_\cA$ decomposes into three
colour sectors:
\[
\Theta^{\oc}_\cA
\;=\;
\Theta^{\mathrm{cl}}_\cA
\;+\;
\Theta^{\mathrm{op}}_\cA
\;+\;
\Theta^{\mathrm{mix}}_\cA,
\]
with the closed sector $\Theta^{\mathrm{cl}}$ encoding bulk
data, the open sector $\Theta^{\mathrm{op}}$ encoding boundary
data, and the mixed sector $\Theta^{\mathrm{mix}}$ encoding
the bulk-to-boundary action. The MC equation
$D\Theta^{\oc} + (1/2)[\Theta^{\oc}, \Theta^{\oc}] = 0$
decomposes by colour:
\begin{align*}
&\text{closed:}\quad
D_{\mathrm{cl}}\Theta^{\mathrm{cl}}
+ \tfrac{1}{2}[\Theta^{\mathrm{cl}}, \Theta^{\mathrm{cl}}]_{\mathrm{cl}} = 0,\\
&\text{open:}\quad
D_{\mathrm{op}}\Theta^{\mathrm{op}}
+ \tfrac{1}{2}[\Theta^{\mathrm{op}}, \Theta^{\mathrm{op}}]_{\mathrm{op}}
+ [\Theta^{\mathrm{mix}}, \Theta^{\mathrm{mix}}]_{\mathrm{op}} = 0,\\
&\text{mixed:}\quad
D_{\mathrm{mix}}\Theta^{\mathrm{mix}}
+ [\Theta^{\mathrm{cl}}, \Theta^{\mathrm{mix}}]_{\mathrm{mix}}
+ [\Theta^{\mathrm{op}}, \Theta^{\mathrm{mix}}]_{\mathrm{mix}} = 0.
\end{align*}
The closed equation is the genus tower of Sections~1--9;
the open equation determines the boundary $A_\infty$ structure
with corrections from mixed-sector interactions; the mixed
equation is the compatibility between bulk and boundary.

\medskip\noindent\textbf{Example 1: Abelian CS ($U(1)$, level $k$).}\enspace
$\Theta^{\mathrm{cl}} = k \cdot \eta \otimes \Lambda$
(scalar, the Heisenberg MC element);
$\Theta^{\mathrm{op}} = 0$ (the boundary algebra $\cH_k$ is
strict, no $A_\infty$ corrections);
$\Theta^{\mathrm{mix}} = 0$ (no bulk-to-boundary action beyond
the identity). Class $\mathbf{G}$: the full 3d MC element
collapses to its closed sector.

\medskip\noindent\textbf{Example 2: Non-abelian CS ($SL_2$, level $k$).}\enspace
$\Theta^{\mathrm{cl}}$ contains the Casimir $r$-matrix
$k\,\Omega/z$ at degree $2$ and the Lie bracket at degree $3$;
$\Theta^{\mathrm{op}}$ encodes the $A_\infty$ structure on
$Y^{\dg}(\mathfrak{sl}_2)$; $\Theta^{\mathrm{mix}}$ encodes
the evaluation map $\mathrm{ev}\colon Y(\mathfrak{sl}_2) \otimes
V \to V$ by which the Yangian acts on evaluation modules.
Class $\mathbf{L}$: the shadow tower terminates at degree $3$
in the closed sector, but the open sector carries the full
Yangian $A_\infty$ structure to all degrees. The Yangian side is
infinite even when the shadow tower is finite.

\medskip\noindent\textbf{Example 3: 3d gravity ($\Vir_c$).}\enspace
$\Theta^{\mathrm{cl}}$ is the infinite shadow tower:
$\kappa = c/2$ at degree $2$, the Virasoro bracket at degree $3$,
$10/[c(5c+22)]$ at degree $4$, and infinitely many higher
corrections. $\Theta^{\mathrm{op}}$ encodes the gravitational
$A_\infty$ structure, which is infinite (class $\mathbf{M}$);
$\Theta^{\mathrm{mix}}$ encodes the action of the gravitational
bulk on the Virasoro boundary. The coproduct
$\Delta_z^{\Vir} = 0$ at all degrees: the ghost-number
obstruction from DS reduction kills every HPL tree correction.
Class $\mathbf{M}$: all three sectors are infinite.

\subsection*{10.12.\enspace Three holographic datums}

\noindent\emph{Abelian CS} ($U(1)$, level $k$): boundary
$\cH_k$, bulk $= \cH_k$, $R(z) = e^{k\hbar/z}$ (scalar,
YBE trivial), $\kappa = k$. Class~$\mathbf{G}$: the entire
holographic datum collapses to the single scalar~$k$.

\smallskip
\noindent\emph{Non-abelian CS} ($SL_2$, level $k$): boundary
$\widehat{\mathfrak{sl}}_2{}_k$, line dual
$\Ydg(\mathfrak{sl}_2)$, $r(z) = k\,\Omega/z$ (vanishing at
$k = 0$), $\kappa = 3(k{+}2)/4$. Evaluation-module
spectral braiding $= U_q(\mathfrak{sl}_2)$ at
$q = e^{i\pi/(k+2)}$. Class~$\mathbf{L}$: the Jacobi identity
kills the shadow tower at degree~$3$.

\smallskip
\noindent\emph{3d gravity} ($SL(2,\bR) \times SL(2,\bR)$
CS, $c = 3\ell/(2G)$): boundary $\Vir_c$, Koszul dual
$\Vir_{26-c}$ (self-dual at $c = 13$), $r(z) = (c/2)/z^3 +
2T/z$, $\kappa = c/2$. Quartic contact
$10/[c(5c{+}22)]$; infinite tower (class~$\mathbf{M}$); the
shadow reads as the gravitational perturbation series. Page
time $t_P = 3S_{\mathrm{BH}}/13$ is $c$-independent because
$\kappa(\Vir_c) + \kappa(\Vir_{26-c}) = 13$. The climax of
Volume~II.


% ====================================================================
\section*{11.\quad Modular PVA quantization}
% ====================================================================

The open/closed world supplies a genus-zero datum: the
Swiss-cheese MC element $\alpha_T$, the PVA
$(\mu, \{-_\lambda -\})$ on cohomology, the KZ/BPZ shadow
connections at degree $n$. All are tree-level. How does this
structure extend across the genus filtration? The answer is
a genus-by-genus obstruction theory whose input is the genus-$0$
PVA and whose output is the full modular MC element. The
nonseparating degeneration operator $D_1$ is the primitive
genus-raising differential; it squares to zero, anticommutes
with the tree-level differential $D_0$, and defines a spectral
sequence whose obstructions are the quantisation anomalies.

\subsection*{11.1.\enspace One-edge principle}

Every nontrivial modular obstruction theory must contain a
primitive genus-raising operator; otherwise any genus-$0$ MC
element lifts tautologically to all genera. The one-edge
expansion
\[
D_{\exp} \;=\; D_{\sep} + D_{\nsep},
\qquad
D_0 \;=\; D_{\mathrm{int}} + D_{\sep},
\qquad
D_1 \;=\; D_{\nsep}
\]
separates genus-preserving from genus-raising degenerations.
$(D_0 + D_1)^2 = 0$ stratifies by genus shift:
$D_0^2 = 0$, $D_0 D_1 + D_1 D_0 = 0$, $D_1^2 = 0$. Trees
govern chirality; loops govern modularity. The three
identities are codim-2 cancellation stratified by genus.

\subsection*{11.2.\enspace Modular bar datum}

A modular bar datum on a reduced complete graded collection
$F \mapsto C(F)$ consists of (i)~an internal differential
$d\colon C(F) \to C(F)$ with $d^2 = 0$;
(ii)~for every one-edge expansion
$\epsilon \in \mathrm{OE}(F)$ (separating or nonseparating), a
degree-$+1$ map
\[
\Delta_\epsilon\colon
sC(F)
\;\longrightarrow\;
\orline(\epsilon) \otimes \bigotimes_{u \in V(\epsilon)}
sC(\Fl_\epsilon(u));
\]
(iii)~the codim-$2$ cancellation
$\sum_{\epsilon_1, \epsilon_2} \sgn\,
\Delta_{\epsilon_2}\circ\Delta_{\epsilon_1} = 0$
for every two-edge graph; and
(iv)~$d\circ\Delta_\epsilon + \Delta_\epsilon\circ d = 0$.
The total $D = d + \sum_\epsilon \Delta_\epsilon$ satisfies
$D^2 = 0$ by three mechanisms: $d^2 = 0$, anticommutation,
and the codim-$2$ axiom. This is the algebraic incarnation
of the cell decomposition of $\overline\cM_{g,n}$ into
stable-graph strata.

\subsection*{11.3.\enspace Complete modular bar coalgebra}

For a connected stable graph $\Gamma$ of genus $g$, set
\[
C[\Gamma]
\;=\;
\orline(\Gamma) \otimes
\bigotimes_{v \in V(\Gamma)} sC(\Fl(v)),
\qquad
\orline(\Gamma) = \bigotimes_{e} \orline(e).
\]
The complete modular bar coalgebra is
\[
\mathbf B_{\mod}(C)
\;=\;
\prod_{[\Gamma] \in \mathsf{StGraph}^{\conn}}
(C[\Gamma])_{\Aut(\Gamma)},
\]
completed over total genus $g(\Gamma) = b_1 + \sum_v g(v)$.
Edge contraction is the reduced coproduct; the coalgebra is
conilpotent.

\subsection*{11.4.\enspace Strict modular deformation algebra}

$L_{\mod}(C) := \Coder(\mathbf B_{\mod}(C))[-1]$ is complete
filtered by genus, with convolution
$L_{\mod}(C) \cong \Hom(\mathbf B_{\mod}(C), sC)[-1]$ under
commutator bracket. The algebra is pro-nilpotent in
$F^1$, and the associated graded inherits a dg Lie structure
at each genus.

\subsection*{11.5.\enspace Genus-$1$ obstruction theorem}

For a genus-$0$ MC element
$\Theta_0 \in \MC(\gr_F^0 L)$, the genus-$1$ obstruction is
\[
\Ob_1(\Theta_0)
\;=\;
[D_1 \Theta_0]
\;\in\;
H^2((\gr_F^1 L)^{\Theta_0}, d_0^{\Theta_0}).
\]
$D_1\Theta_0$ is a $d_0^{\Theta_0}$-cocycle by
$D_0 D_1 + D_1 D_0 = 0$ and the MC equation for $\Theta_0$.
The class vanishes iff $\Theta_0$ lifts to
$\Theta_0 + \hbar\Theta_1$ satisfying the modular MC equation
modulo $\hbar^2$.

In PVA coordinates, the nonseparating one-edge operator acts
as the reduced odd Laplacian: for cyclic $(A, m_k, \langle-,-\rangle)$
with basis $\{e^i\}$ and dual basis $\{e_i\}$,
\[
\ell_1^{(1)}(a)
\;=\;
\hbar\Delta_{\mathrm{cyc}}(a)
\;=\;
\hbar\sum_i m_2(e^i, m_2(a, e_i)).
\]
The full $\Ob_1$ is the cohomology class of
$\Delta_{\mathrm{cyc}}(\Theta_0)$.

\medskip
\noindent\textbf{Heisenberg: $\Ob_1 = 0$ trivially.}\enspace
For $\cH_k$: $m_k = 0$ for $k \ge 3$, so
$\Delta_{\mathrm{cyc}}(\Theta_{\cH_k}) = \hbar \sum_i
m_2(e^i, m_2(\Theta_0, e_i))$. But $\Theta_0 = k \cdot
\eta_{\mathrm{univ}} \otimes \Lambda_{\mathrm{univ}}$ is a
scalar, so $m_2(\Theta_0, e_i) = k \cdot e_i$ and
$m_2(e^i, k \cdot e_i) = k^2 \cdot \delta^i_i$. The trace
gives $\Delta_{\mathrm{cyc}}(\Theta_0) = \hbar k^2 \cdot
\dim(V)$: a scalar, hence $d_0$-closed and $d_0$-exact (it is
the curvature $\kappa \cdot \omega_1$ in the bar complex, which
is absorbed by the Gauss--Manin connection). Obstruction zero;
the Heisenberg lifts to all genera with no quantum correction.
Class~$\mathbf{G}$: the simplest possible modular behaviour.

\medskip
\noindent\textbf{Kac--Moody: $\Ob_1 = 0$ by Whitehead.}\enspace
For $\widehat{\fg}_k$: $\Delta_{\mathrm{cyc}}(\Theta_0)$
involves $m_3$ and the Lie bracket $f^{ab}{}_c$. The
obstruction class lives in $H^2(\fg; \Sym^q V)$ for reductive
$\fg$; Whitehead's lemma kills $H^2$ for semisimple $\fg$.
The genus-$1$ lift exists unconditionally for all simple types.
Class~$\mathbf{L}$: Whitehead is the mechanism.

\medskip
\noindent\textbf{Virasoro: $\Ob_1 = 0$ by central direction.}\enspace
For $\Vir_c$: $\Delta_{\mathrm{cyc}}(\Theta_0)$ involves the
self-coupling $T_{(1)}T = 2T$ and the quartic pole $T_{(3)}T = c/2$.
The contraction $\sum_i m_2(T^i, m_2(\Theta_0, T_i))$ produces a
linear combination of $T\partial T$, $\partial^3 T$, and
$c \cdot \mathbf{1}$. The quasi-primary projection kills the
total-derivative terms ($\partial^3 T$ and $T\partial T$ project to
$\Lambda$ and a quasi-primary correction); what survives is a
scalar proportional to $c$ times the central direction
$\partial_c$. Since $H^1((\gr^1 L)^{\Theta_0}, d_0^{\Theta_0})
\cong \bC \cdot \partial_c$, the class is $d_0$-exact:
$\Ob_1(\Theta_0) = 0$. The genus-$1$ lift exists as a
renormalisation of the central charge: $c \mapsto c + \hbar c_1$
with $c_1$ determined by the one-loop computation.
Class~$\mathbf{M}$: the central direction absorbs the obstruction
at every genus individually, but the full tower is infinite.

\medskip
\noindent\textbf{$\beta\gamma$: $\Ob_1 = 0$ by ghost-number
grading.}\enspace
For $\beta\gamma_\lambda$: the fields $\beta$ and $\gamma$ carry
opposite ghost numbers ($+1$ and $-1$). The cyclic Laplacian
$\Delta_{\mathrm{cyc}}(\Theta_0)$ involves contracting $\beta$
with $\gamma$ through the cyclic pairing; the ghost-number
selection rule forces the contraction to land in ghost number
$0$, which is the scalar sector. The obstruction is a scalar
multiple of $\mathbf{1}$, hence $d_0$-exact.
Class~$\mathbf{C}$: the ghost-number grading is the mechanism,
distinct from both the scalar absorption (class $\mathbf{G}$)
and the Whitehead vanishing (class $\mathbf{L}$). The
$\beta\gamma$ system provides the third independent vanishing
mechanism for the genus-$1$ obstruction.

\subsection*{11.6.\enspace The quantisation theorem}

\begin{theorem}[Modular PVA quantisation]
For a chirally Koszul, positive-energy, finitely strongly
generated chiral algebra $\cA$ with $\kappa(\cA) \neq 0$, the
genus-$0$ MC element $\Theta_0 \in \MC(\gr^0_F L_{\mod})$ lifts
to a full modular MC element
$\Theta = \sum_{g \ge 0} \hbar^g \Theta_g
\in \MC(L_{\mod})$
satisfying the quantum master equation at all genera. The lift
is unique up to gauge equivalence in
$\exp(F^1 L_{\mod})$.
\end{theorem}

\noindent
The proof proceeds genus-by-genus. At each genus $g$, the
obstruction to extending $\Theta^{< g}$ to genus $g$ is a
class $[\Ob_g] \in H^2(\gr^g_F L_{\mod}^{\Theta^{<g}},
d_0^{\Theta^{<g}})$. The class is computed by the formula
\[
\Ob_g(\Theta^{<g})
\;=\;
\sum_{\substack{\Gamma \in \mathsf{StGraph}_{g,0} \\
b_1(\Gamma) = g}}
\frac{1}{|\Aut(\Gamma)|}
W_\Gamma(\Theta^{<g}),
\]
where the sum runs over connected stable graphs of genus $g$
with no legs and first Betti number $g$. The vanishing of
$[\Ob_g]$ is proved by three independent mechanisms depending
on the depth class:
\begin{itemize}[nosep]
\item Class $\mathbf{G}$ (Heisenberg, lattice):
$\Ob_g = 0$ at all $g$ because $m_k = 0$ for $k \ge 3$;
every graph with an internal vertex of valence $\ge 3$
vanishes.
\item Class $\mathbf{L}$ (affine KM):
$\Ob_g = 0$ by the Whitehead lemma at each genus: the
obstruction class lives in $H^2(\fg; M_g)$ for a
$\fg$-module $M_g$ determined by lower-genus data, and
$H^2 = 0$ for semisimple $\fg$.
\item Class $\mathbf{M}$ (Virasoro, $\cW_N$):
$\Ob_g = 0$ in cohomology (proved); the chain-level lift
at genus $g$ requires the harmonic mechanism
$\delta_r^{\mathrm{harm}} = c_r(\cA) \cdot m_0^{\lfloor r/2 \rfloor - 1}$
from Hodge decomposition. For class $\mathbf{M}$,
the chain-level lift is conjectural at $g \ge 2$; the
coderived formulation is clean.
\end{itemize}

Uniqueness: at each genus, the space of lifts modulo gauge
is an affine space under $H^1(\gr^g_F L^{\Theta^{<g}})$. For
standard families this space is one-dimensional (spanned by
$\partial_c$ or $\partial_k$), so the lift is unique up to
reparametrisation of the central charge.

\subsection*{11.7.\enspace $\cW_3$ computation in detail}

A filtered quadratic PVA is generated by $u^1, \ldots, u^N$ with
$\lambda$-bracket $\Pi^{ab}(\partial)$ of total generator degree
$\le 2$. Classical $\cW_3$ fits: generators $T$ (weight $2$),
$W$ (weight $3$), with the composite
$\Lambda = :TT: - (3/10)\partial^2 T$ controlling the nonlinear
channel; the $WW$ OPE has the $c = -22/5$ pole in
$16/(22 + 5c)$ where $\Lambda$ becomes null.

\medskip\noindent\textbf{The $WW$ lambda-bracket.}\enspace
In lambda-bracket notation (Vol~II convention):
\begin{align*}
\{W_\lambda W\}
&= \frac{c}{3}\lambda^5
+ 2T\lambda^3
+ T'\lambda^2
+ \Bigl[\frac{16}{22+5c}\Lambda
+ \frac{3}{10}T''\Bigr]\lambda\\
&\quad + \Bigl[\frac{8}{22+5c}\Lambda'
+ \frac{1}{15}T'''\Bigr],
\end{align*}
where $\Lambda = :TT: - (3/10)T''$ and primes denote
$\partial$-derivatives. The coefficient
$\alpha(c) = 16/(22 + 5c)$ is fixed uniquely by
quasi-primarity ($L_1 \Lambda = 0$) and the Jacobi identity for
the triple $\{W, W, W\}$. At $c = -22/5$: $\alpha \to \infty$,
$\Lambda$ becomes null, and $\cW_3$ degenerates (the $(2,5)$
minimal model). At $c = 0$: $\alpha = 16/22 = 8/11$, a finite
value corresponding to the free-field limit.

\medskip\noindent\textbf{The genus-$1$ obstruction.}\enspace
The genus-$1$ obstruction for $\cW_3$ decomposes into three
channels:
\[
\Ob_1(\Theta_0^{\cW_3})
\;=\;
\Ob_1^{TT} + \Ob_1^{TW} + \Ob_1^{WW}.
\]
The $TT$ channel is the Virasoro genus-$1$ obstruction
(vanishes by the same mechanism as for $\Vir_c$ alone). The
$TW$ cross-channel vanishes by conformal weight parity: the
fields $T$ and $W$ have weights $2$ and $3$ (different parity),
forcing the contraction $\sum_i m_2(T^i, m_2(\Theta_0^{TW}, T_i))$
to zero by grading. The $WW$ channel: the key computation.
The contraction $\Delta_{\mathrm{cyc}}(\Theta_0^{WW})$ produces
terms involving $\Lambda$ and $T''$; the
$W$-normal form (expressing everything in the basis
$\{T, W, \Lambda, T'', \ldots\}$ with $\Lambda$ as the
independent weight-$4$ quasi-primary) reduces the obstruction to
a single scalar proportional to $\partial_c$.

The triangular $W$-normal form vanishing theorem: in the local,
translation-invariant, filtration-preserving sector,
$\Ob_1(\Theta_0) = 0$ for classical $\cW_3$. The relevant
cohomology is
$H^1((\gr^1 L)^{\Theta_0}, d_0^{\Theta_0})
\cong \bC\cdot\partial_c P_c$,
one-dimensional and spanned by the central-parameter direction.
Every genus-$1$ lift is gauge equivalent to a renormalisation
$c \mapsto c + \hbar c_1$; the genus-$1$ quantum $\cW_3$ is the
unique quantisation in the direction $\partial_c$.

\medskip\noindent\textbf{Genus-$2$ cross-channel
obstruction.}\enspace
At genus $2$, the $\cW_3$ obstruction has a genuinely new
feature: the $TW$ cross-channel contributes. The seven
genus-$2$ stable graphs produce seven graph amplitudes, and the
cross-channel correction
$\delta F_2^{\cross}(\cW_3)$ is nonzero. The universal formula:
\[
\delta F_2^{\grav}(\cW_N, c)
\;=\;
\frac{(N-2)(N+3)}{96}
+ \frac{(N-2)(3N^3 + 14N^2 + 22N + 33)}{24c}.
\]
At $N = 2$: $\delta F_2^{\grav} = 0$ (Virasoro is single-generator,
no cross-channel). At $N = 3$:
$\delta F_2^{\grav}(\cW_3, c) = 5/96 + (c + 204)/(16c)$.
The scalar uniform-weight formula
$F_g = \kappa \cdot \lambda_g^{\FP}$ fails at $g \ge 2$ for
multi-weight algebras \textsc{(all-weight, with cross-channel
correction)}.

\subsection*{11.8.\enspace The Khan--Zeng sigma model}

Khan and Zeng construct a 3d holomorphic-topological Poisson
sigma model that realises the modular PVA quantisation programme
geometrically. The construction applies to every freely generated
PVA with conformal vector. The field content on
$\bR_+ \times \bC$:
\begin{itemize}[nosep]
\item $A_{\bar z} \in \Omega^{0,1}(\bC) \otimes \fg$: the
$(0,1)$-form field (holomorphic gauge field).
\item $\phi \in \Omega^0(\bC) \otimes \fg^*$: the scalar field
(conjugate momentum).
\item $\eta \in \Omega^1(\bR_+) \otimes \fg$: the topological
$1$-form on the half-line (boundary condition data).
\end{itemize}
The action functional:
\[
S_{\KZ}
\;=\;
\int_{\bR_+ \times \bC}
\Bigl(
\langle\phi, \bar\partial A\rangle
+ \langle\phi, \tfrac{1}{2}\{A_\lambda A\}|_{\lambda=0}\rangle
+ \langle\eta, d_t \phi\rangle
\Bigr)
\,dt \wedge dz \wedge d\bar z.
\]
Gauge invariance is the PVA Jacobi identity: the variation
$\delta S_{\KZ} = 0$ under
$\delta A = \bar\partial\epsilon + \{A_\lambda \epsilon\}|_{\lambda=0}$
requires exactly the Jacobi identity for
$\{-_\lambda -\}$, the Leibniz rule for $\mu$, and the
sesquilinearity of the bracket. A conformal vector promotes the
holomorphic-topological theory to topological: the Sugawara
construction $T = \{Q, G\}$ makes $\bC$-translations $Q$-exact,
collapsing the holomorphic direction in cohomology.

The boundary theory on $\{0\} \times \bC$ carries a
$(-1)$-shifted Poisson bracket; the quantisation of this bracket
is the genus-$0$ MC problem. The bulk theory on
$\bR_+ \times \bC$ provides the genus-raising mechanism: loops
in the bulk produce traces on the boundary, and the genus-$g$
obstruction $\Ob_g$ is the $g$-loop Feynman integral in the
bulk sigma model. The entire modular PVA quantisation programme
is thereby geometrised.

The scope: the Khan--Zeng construction covers all freely generated
PVAs with conformal vector. Before declaring the topologisation
conjecture open for a specific vertex algebra, one checks: is the
associated graded $\gr_{Li}(\cA)$ freely generated? If so, the
$E_3$-topological structure is proved. This covers all affine
Kac--Moody algebras at non-critical level and all principal
$\cW$-algebras.

\subsection*{11.9.\enspace Curved extension via $S$-tails}

In the inhomogeneous quadratic setting (Gui--Li--Zeng), the
correct input is a twisted pair $(B, B^\circ, S)$: a
CDG-algebra $B$, a CDG-coalgebra $B^\circ$, and curvature $S$.
An $S$-tail expansion attaches a univalent $S$-decorated vertex
to a corolla, followed by contraction of the new internal edge.
Adjoining $S$-tail expansions to one-edge expansions with the
same codim-$2$ compatibilities gives a curved modular bar
object. The curved MC equation is
$\mu((S + \alpha) \boxtimes (S + \alpha)) = 0$; at genus $0$
it is the curved $A_\infty$ MC equation with $m_0 = S$, at
genus $1$ it is $\Delta_{\mathrm{cyc}}(S + \alpha) = 0$, and
at genus $g$ it is the BV quantum master equation
$\hbar\Delta(e^{(S+\alpha)/\hbar}) = 0$.

\subsection*{11.10.\enspace Genus-$0$ Gui--Li--Zeng comparison}

At tree level, the modular MC equation reduces to the
classical twisting morphism equation. For a Koszul pair
$(\cA, \cA^!)$ with $\cA^!$ a CDG algebra with curvature $S$,
\[
\MC_0(L_{\mod})
\;\cong\;
\Hom_{\mathsf{dg}}(\cA, B^\circ)
\;\hookrightarrow\;
\MC(\cA^! \widehat\otimes \cB).
\]
The modular theory is the genus extension of the classical
Gui--Li--Zeng picture. The CDG curvature $S$ is the bar-dual of
the vacuum OPE: $m_0 = S \in \barB^0 = \bC$ is the scalar
that records the quartic pole (for Virasoro, $S = c/2$). At
genus $0$: the curved $A_\infty$ relation $m_1^2(a) = [m_0, a]$
is the statement that the bar differential squares to the
commutator with the curvature, not to zero. At genus $g$:
$d_{\mathrm{fib}}^2 = \kappa \cdot \omega_g$ is the fiberwise
statement, with $\kappa = m_0$ the curvature scalar. The
modular theory organises these identities across all genera
simultaneously.


% ====================================================================
\section*{12.\quad Holographic modular Koszul duality}
% ====================================================================

Sections~1--9 construct $E_n$-chiral algebras as
algebraic-geometric objects: bar complexes on configuration
spaces, $R$-matrices, derived chiral centres with $E_2$/$E_3$
structure, the $\SCchtop$ datum on the pair
$(\cZ^{\der}_{\ch}(\cA),\, \cA)$. The physical
interpretation: the derived chiral centre IS the bulk of a real
3d holomorphic-topological gauge theory. The open/closed world
(Section~10) supplies the 3d geometric framework; the modular
PVA quantisation programme (Section~11) supplies the obstruction
theory. The holographic modular Koszul datum packages the
passage from algebraic geometry to physics into a single
six-component structure: boundary algebra, Koszul dual, line
category, spectral $R$-matrix, universal MC element, and modular
shadow connection. Every ingredient constructed in
Sections~1--9 is a projection of this datum. The datum is the
smallest package from which the full physical correspondence
reconstructs.

\subsection*{12.1.\enspace The holographic modular Koszul datum}

Every 3d HT system $T$ is controlled by
\[
\cH(T)
\;=\;
(\cA,\; \cA^!,\; \cC,\; r(z),\; \Theta_\cA,\; \nabla^{\hol}),
\]
where:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\cA$ is the boundary chiral algebra on a curve $X$,
restricted from the holomorphic boundary
$\{0\} \times X \subset \bR_+ \times X$.
\item $\cA^!$ is the strict chiral Koszul dual,
$\cA^! = (\cA^{\mathrm i})^\vee$ with $\cA^{\mathrm i} = H^*(\barB(\cA))$.
Holographically, $\cA^!$ is a dg-shifted Yangian: the bar
complex $\barB(A_b)$ is an $E_1$ coassociative coalgebra, and $\cA^!$ is
its linear dual. The $\SCchtop$ datum is the pair
$(C^\bullet_{\mathrm{ch}}(\cA,\cA),\,\cA)$ of chiral derived center
and boundary algebra.
\item $\cC \simeq \cA^!\text{-mod}$ is the braided tensor
category of line operators: objects are topological defect
lines, morphisms junction operators, braiding from crossing
in the holomorphic plane.
\item $r(z) \in \cA^! \otimes \cA^!(\!(z^{-1})\!)$ is the
classical $r$-matrix satisfying CYBE, the binary genus-$0$
shadow $r(z) = \Res^{\coll}_{0,2}(\Theta_\cA)$.
\item $\Theta_\cA \in \MC(\gAmod)$ is the universal MC element
from the bar-intrinsic construction $\Theta_\cA := D_\cA - d_0$,
always MC because $D_\cA^2 = 0$.
\item $\nabla^{\hol}_{g,n} = d - \mathrm{Sh}_{g,n}(\Theta_\cA)$
is the modular shadow connection on
$\overline\cM_{g,n}$, flat by the MC equation projected to
$(g, n)$.
\end{enumerate}

\subsection*{12.2.\enspace Collision filtration}

The modular convolution $\gAmod$ carries a collision filtration
$F^0_{\coll} \supset F^1_{\coll} \supset \cdots$ indexed by
minimum pairwise distance on $\FM_n(\bC)$. Depth $0$ is
free propagation; depth $1$ is first collision; depth $k$
is $k$-fold nested collision. The spectral sequence has
$E_1^{p,*} = H^*(\gr^p_{\coll}\gAmod, d_0)$ with $d_1$
Arnold cancellations; it converges to $H^*(\gAmod)$, and
collapse is governed by shadow depth: class $\mathbf G$
collapses at $E_2$; class $\mathbf M$ does not collapse at
any finite page.

\subsection*{12.3.\enspace Four proved recovery theorems}

\medskip\noindent\emph{(R1) Collision residue is twisting.}
At depth $1$, degree $2$:
$\Res^{\coll}_{0,2}(\Theta_\cA) = \pi_\cA$, the universal
twisting morphism producing the dg-shifted Yangian $r_\cA(z)$.
The MC equation becomes $\partial\pi + \pi\star\pi = 0$.

\medskip\noindent\emph{(R2) CYBE from Arnold.} The three
boundary divisors of $\overline M_{0,4}$ correspond to channels
$(12|34)$, $(13|24)$, $(14|23)$. Evaluating the Arnold relation
on the Casimir $\Omega\otimes\Omega \in (\cA^!)^{\otimes 3}$
produces the three terms of the CYBE
$\sum [r_{ij}, r_{ik}] = 0$.

\medskip\noindent\emph{(R3) Affine shadow / KZ comparison.}
For $\cA = \widehat\fg_k$, on the affine comparison surface the
genus-$0$ degree-$n$ shadow one-form is the KZ connection form
\[
\mathrm{Sh}_{0,n}(\Theta_{\widehat\fg_k})
\;=\;
\sum_{i < j} r_{ij} \, d\log(z_i - z_j)
\;=\;
\frac{1}{h^\vee + k}\sum_{i < j}
\frac{\Omega_{ij}\,dz_{ij}}{z_{ij}},
\]
where $r_{ij} = \Omega_{ij}/(h^\vee + k)$ is the
propagator-weighted Casimir. Flatness is MC at genus $0$,
degree $n$. For Virasoro, the Virasoro conformal Ward extraction
plus higher collision residues yields the BPZ equations. The
affine Drinfeld--Kohno theorem compares monodromy with the
quantum-group representation category.

\medskip\noindent\emph{(R4) Quartic as $L_\infty$ obstruction.}
$[\mathfrak R^{\mod}_4(\cA)] = [o_4(\cA)]
\in H^2(\cA^{\mathrm{sh}}_{4,0})$ is the obstruction to extending
$r(z)$ from degree $2$ to degree $4$. Vanishes for classes
$\mathbf G, \mathbf L, \mathbf C$; nonzero for class
$\mathbf M$ (Virasoro: $Q^{\contact} = 10/[c(5c+22)]$).

\medskip\noindent\textbf{Recovery theorem table.}\enspace
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{llll}
\textbf{Recovery} & \textbf{Depth} & \textbf{Output} & \textbf{Family}\\ \hline
(R1) Collision residue & $1$ & twisting morphism $\pi_\cA$
 & all\\
(R2) Arnold $\to$ CYBE & $1$ & Yang--Baxter for $r(z)$
 & all\\
(R3) Shadow $\to$ KZ & $0$--$n$ & KZ/BPZ connection
 & KM, Vir\\
(R4) Quartic obstruction & $4$ & $L_\infty$ class
 & class $\mathbf{M}$ only
\end{tabular}
\end{center}

\noindent
Each recovery theorem captures a \emph{different} projection of
$\Theta_\cA$: (R1) the degree-$2$ binary collision; (R2) the
degree-$3$ ternary collision (Arnold relation on three points);
(R3) the full degree-$n$ shadow at genus $0$ (comparing
$n$-point collisions with KZ monodromy); (R4) the degree-$4$
obstruction (the first nonlinear invariant). Together they
reconstruct the full genus-$0$ MC element from its
finite-degree projections.

\medskip\noindent\textbf{Critical level recovery.}\enspace
At the critical level $k = -h^\vee$ for affine Kac--Moody:
$\kappa = 0$, all monodromy is trivial (integer eigenvalues from
the Sugawara formula at $k = -h^\vee$), and $H^1$ doubles
(from $4$ to $8$ dimensions for $\mathfrak{sl}_2$). The
spectral sequence $E_1^{p,q}$ has $d_1 = \lambda \cdot [\delta]$
vanishing at $\lambda = 0$ (the critical specialisation); the
Feigin--Frenkel centre
$\mathfrak{z}(\widehat\fg_{-h^\vee}) \cong \Fun(\Op_{{}^L\fg}(D))$
emerges as the bar cohomology at critical level.

\subsection*{12.4.\enspace Five conjectural targets}

\begin{enumerate}[label=(\roman*)]
\item \emph{Boundary-defect realisation.} $\cA_\partial(T)$
and $\cA^!_\partial(T)$ are the two algebras of $\cH(T)$ for
every 3d HT system, with $\cC \simeq \cA^!\text{-mod}$.
\item \emph{Yangian-shadow.} In full derived generality, the
collision residue recovers the dg-shifted Yangian $r(z)$ at
the chain level, including higher $A_\infty$ homotopies.
\item \emph{Sphere reconstruction.} The Gaiotto--Zeng (2026)
commuting differentials on the non-planar sphere algebra are
the scalar shadow $\mathrm{Sh}_{0,n}(\Theta_\cA)$; sphere
amplitudes are flat sections of $\nabla^{\hol}_{0,n}$ on
established comparison surfaces.
\item \emph{Quartic resonance obstruction.}
$\mathfrak R^{\mod}_4$ is the first global nonlinear invariant,
measuring the failure of the large-$N$ expansion to truncate
at tree level.
\item \emph{Singular-fibre descent.}
$\nabla^{\hol}|_{\partial\overline\cM} \sim \nabla^{\clutch}$
with residues from the clutching law of $\Theta_\cA$:
$\Theta_\cA|_{\sigma_\Gamma} = \prod_v \Theta_v \cdot \prod_e P_e$.
\end{enumerate}

\subsection*{12.5.\enspace Coloured modular deformation object}

A 3d HT theory produces three observation algebras:
$\Obs^{\hol}$ (bulk), $\Obs^\partial$ (boundary), $\Obs^\ell$
(line). The coloured Swiss-cheese FM space
$\FM^{\log}_{\bullet, \SC}$ encodes the collision geometry of
all three. The three-colour modular deformation object is
\[
\fg^{\mathrm{HT},\log}_{\mod}
\;=\;
\hom^{\alpha_{\mathrm{HT}}}\!\bigl(
C_\bullet(\FM^{\log}_{\bullet, \SC}),
\End_{\Ch_\infty}(\Obs^{\hol}_\infty, \Obs^\partial_\infty,
\Obs^\ell_\infty)\bigr).
\]
The three colours interact through $\SCchtop$: bulk-to-boundary,
boundary-to-line, no line-to-bulk.

The modular effective action is the graph sum
\[
S^{\mod}_{\mathrm{HT}}
\;=\;
\sum_{\Gamma \in \mathsf{StGraph}_{\SC}}
\frac{\hbar^{b_1(\Gamma)}}{|\Aut(\Gamma)|}
W^{\log}_\Gamma O_\Gamma,
\]
and the BV quantum master equation
$(d_{\BV} + \hbar\Delta_{\mathrm{odd}})\exp(S^{\mod}/\hbar) = 0$
is the single equation governing $T$. At genus $0$: classical
BV $\{S_0, S_0\} = 0$; genus $1$: one-loop anomaly cancellation;
genus $g$: $g$-loop Ward identity.

\subsection*{12.6.\enspace Khan--Zeng bridge}

Khan and Zeng construct a 3d HT Poisson sigma model on
$\bR_+ \times \bC$ attached to a freely generated PVA:
$\fg$-valued $(0,1)$-form $A_{\bar z}$, $\fg^*$-valued scalar
$\phi$, $\fg$-valued $1$-form $\eta$ on $\bR_+$, with action
\[
S_{\KZ}
\;=\;
\int_{\bR_+\times\bC}
(\langle\phi, \bar\partial A\rangle
+ \langle\phi, \tfrac12\{A_\lambda A\}|_{\lambda=0}\rangle
+ \langle\eta, d_t\phi\rangle)\,dt\wedge dz\wedge d\bar z.
\]
Gauge invariance is the PVA Jacobi identity; a Virasoro
element promotes HT to topological; the boundary carries a
$(-1)$-shifted Poisson bracket and generates the genus-$0$
quantisation problem. The modular extension couples the
bulk theory to stable curves at $g \ge 1$ and controls the
full genus tower. The pipeline:
\[
\text{classical coisson}
\;\xrightarrow{\text{KZ quantisation}}\;
\text{genus-$0$ quantum Koszul}
\;\xrightarrow{\text{modular lift}}\;
\cH(T).
\]

The bridge is completed in Volume~II by the doubling theorem:
the half-space BV problem for any logarithmic $\SCchtop$-algebra
embeds into the doubled whole-space via method of images; the
reflected weight identity is the $\sigma$-invariant restriction
of the standard Stokes identity on the doubled FM compactification.
The affine Poisson--vertex sigma model satisfies the physics
bridge hypotheses, and Drinfeld--Sokolov reduction preserves
this structure. The entire standard landscape enters through
these two gates.

The genus expansion of the modular bar differential,
$D = \sum_{g \ge 0} \hbar^g D^{(g)}$, is the Feynman transform
of the modular operad; the canonical MC element
$\delta_\cA = D - D^{(0)}$ computes positive-genus corrections.
Stable graphs, automorphism weights, genus bookkeeping: the
mathematical shadow of the 't~Hooft expansion. The
identification $\hbar \leftrightarrow 1/N$ for a specific
holographic model remains the principal open bridge.

\subsection*{12.7.\enspace Heisenberg holographic datum}

Base case: shadow class $\mathbf G$, shadow depth $2$, trivial
line-operator category, scalar $R$-matrix. For $\cA = \cH_k$:
\begin{align*}
\cA &= \cH_k, & \cA^! &= \Sym^{\ch}(V^*),
 & \cC &= \mathsf{Vect},\\
r(z) &= k/z, & R(z) &= \exp(k/z),
 & \Theta_{\cH_k} &= k\cdot\eta\otimes\Lambda.
\end{align*}
The shadow connection $\nabla^{\hol}_{g,n} = d$ is trivial
(scalar MC element). All five conjectural targets are
trivially verified: free boundary, curved symmetric dual
(with $\cH_k^! \neq \cH_{-k}$, $m_0 = -k\omega$), trivial
lines, vanishing quartic, no moduli dependence.

\subsection*{12.8.\enspace Affine $\widehat{\mathfrak{sl}}_2$ holographic datum}

First nontrivial example: class $\mathbf L$, shadow depth $3$,
Yang's $r(z) = k\,\Omega/z$, line-operator category
$Y(\mathfrak{sl}_2)\text{-mod}$, KZ shadow connection,
quantum-group representation theory from genus-$0$ monodromy.
\[
\cH(\widehat{\mathfrak{sl}}_2{}_k)
\;=\;
\Bigl(
\widehat{\mathfrak{sl}}_2{}_k,\;
\widehat{\mathfrak{sl}}_2{}_{-k-4},\;
\cO_q^{\mathrm{sh}},\;
\tfrac{k\,\Omega}{z},\;
\Theta_k,\;
d - \kappa_k\,\omega_g
\Bigr),
\]
with $q = e^{i\pi/(k+2)}$ and $\kappa_k = 3(k+2)/4$. At
$k = -2$: $\kappa = 0$, the Feigin--Frenkel centre is the
algebra of $\mathfrak{sl}_2$-opers. The KZ monodromy is
compared with the $U_q(\mathfrak{sl}_2)$ $R$-matrix by affine
Drinfeld--Kohno; on the reduced evaluation comparison surface,
$\cC_{\mathrm{line}}^{\red}|_{\mathrm{eval}}$ is identified
with the corresponding quantum-group side, and the coloured
Jones polynomial is recovered from monodromy of the bar complex
(Steinberg convolution of the chiral self-intersection on
$\FM_k(\bC)$).

This is 3d Chern--Simons at level $k$. The holographic datum
is the $k = 0$-vanishing $r$-matrix plus the full KZ package.

\subsection*{12.9.\enspace Virasoro holographic datum}

First example of shadow class $\mathbf M$. The $r$-matrix
$r_c(z) = (c/2)/z^3 + 2T/z$ has both a third-order pole
(gravitational) and a first-order pole (stress-tensor
exchange); the quartic contact invariant
$Q^{\contact} = 10/[c(5c+22)] \neq 0$. The datum packages
3d gravity on $\bR_+ \times \bC$:
\begin{align*}
\cH(\Vir_c)
&\;=\;
(\Vir_c,\; \Vir_{26-c},\; \cC_c,\; r_c(z),\; \Theta_c,\;
\nabla^{\hol}_c),\\
r_c(z) &\;=\; \frac{c/2}{z^3} + \frac{2T}{z},
\qquad
\kappa_c \;=\; \frac{c}{2},\\
\nabla^{\hol}_{1,1}
&\;=\; d \;-\; \kappa_c\,\omega_1
\;-\; \frac{10}{c(5c+22)}\,\delta_4 \;-\; \cdots.
\end{align*}
Koszul dual $\Vir_{26-c}$ (self-dual at $c = 13$, not $c = 26$);
shadow connection with curvature $\kappa_c\omega_g$ at leading
order. The transferred coproduct $\Delta_z^{\Vir}$ is strictly
primitive at all degrees
(Principle~\ref{princ:gravitational-primitivity}): ghost-number
obstruction intrinsic to DS reduction kills every HPL tree
correction. All gravitational dynamics resides in the
collision residue and the infinite $A_\infty$ product tower;
the coproduct channel is identically zero. Gravity does not
produce particles, only braids them.

\medskip\noindent\textbf{The six components in full.}\enspace
\begin{enumerate}[label=(\roman*),nosep]
\item $\cA = \Vir_c$: the Virasoro algebra at central charge $c$,
generated by $T$ of weight $2$. The OPE
$T(z)T(w) \sim (c/2)/(z-w)^4 + 2T(w)/(z-w)^2 + \partial T(w)/(z-w)$
has three pole orders. The three pole orders produce: at order $4$,
the curvature $m_0 = c/2$; at order $2$, the self-coupling
$T_{(1)}T = 2T$ driving infinite depth; at order $1$, the
translation $T_{(0)}T = \partial T$.

\item $\cA^! = \Vir_{26-c}$: the Koszul dual, obtained by
$c \mapsto 26 - c$ (Feigin--Frenkel involution). Koszul
complementarity (Virasoro branch):
$\kappa(\Vir_c) + \kappa(\Vir_{26-c}) = c/2 + (26-c)/2 = 13$.
Self-dual at $c = 13$. The critical dimension $c = 26$ is where
the \emph{dual} curvature vanishes:
$\kappa(\Vir_{26-c})|_{c=26} = 0$; the algebra itself retains
$\kappa = 13$. At $c = 0$: $\kappa = 0$ and $\kappa' = 13$.

\item $\cC_c$: the line-operator category. For large $c$,
this should be the category of modules over a
$\cW_\infty$-type Yangian; at specific rational $c$
(minimal models), $\cC_c$ is a finite semisimple category
(the $(p,q)$ fusion category). The spectral braiding is
the $E_1$ ordered structure.

\item $r_c(z) = (c/2)/z^3 + 2T/z$: the classical $r$-matrix.
The $d\log$ absorption of the OPE drops each pole order by $1$:
quartic $\to$ cubic, quadratic $\to$ simple. The cubic pole
$c/(2z^3)$ is the gravitational sector; the simple pole $2T/z$ is
the stress-tensor exchange. At $c = 0$: $r_0(z) = 2T/z$ (the
curvature vanishes but the self-coupling persists). The CYBE
is the Arnold relation evaluated on the stress-tensor Casimir.

\item $\Theta_c = \sum_{r \ge 2} \Theta_c^{(r)}$: the universal
MC element. Its low-degree projections:
\begin{align*}
\Theta_c^{(2)} &= (c/2) \cdot \eta \otimes \Lambda
 &&\text{(curvature)},\\
\Theta_c^{(3)} &= \text{Virasoro bracket}
 &&\text{(Lie structure of } T_{(1)}T = 2T\text{)},\\
\Theta_c^{(4)} &= \frac{10}{c(5c+22)} \cdot \delta_4
 &&\text{(quartic contact)},\\
\Theta_c^{(5)} &= \frac{480}{c^2(5c+22)} \cdot x^5
 &&\text{(quintic obstruction, nonzero)}.
\end{align*}
The quintic $\Theta_c^{(5)} \neq 0$ proves infinite depth: no
finite truncation captures $\Theta_c$.

\item $\nabla_c^{\hol} = d - \mathrm{Sh}_{g,n}(\Theta_c)$:
the shadow connection. At $(g,n) = (1,1)$:
\[
\nabla^{\hol}_{1,1}
\;=\; d - \frac{c}{2}\omega_1
- \frac{10}{c(5c+22)}\delta_4
- \frac{480}{c^2(5c+22)}\delta_5 - \cdots.
\]
Flatness $(\nabla^{\hol})^2 = 0$ is the MC equation projected
to $(g,n)$; it holds at all genera simultaneously.
\end{enumerate}

\medskip\noindent\textbf{Distinguished values of $c$.}\enspace
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{llll}
$c$ & $\kappa$ & $Q^{\contact}$ & Physics\\ \hline
$0$ & $0$ & $\infty$ & free field; curvature vanishes\\
$1$ & $1/2$ & $10/27$ & single free boson\\
$13$ & $13/2$ & $10/(13\cdot 87)$ & self-dual point;
$\kappa = \kappa'$\\
$25$ & $25/2$ & $10/(25 \cdot 147)$ & critical bosonic string\\
$26$ & $13$ & $10/(26 \cdot 152)$ & dual curvature $\kappa'=0$\\
$-22/5$ & $-11/5$ & $\infty$ & $(2,5)$ minimal model;
$\Lambda$ null\\
$\infty$ & $\infty$ & $\sim 2/c^2$ & semiclassical
gravity
\end{tabular}
\end{center}

\medskip\noindent\textbf{Gravitational primitivity.}\enspace
The Drinfeld coproduct $\Delta_z^{\Vir}$ vanishes at all degrees:
$\Delta_z^{\Vir}(T^{(k)}) = 0$ for all $k \ge 0$, where $T^{(k)}$
denotes the $k$-th derivative of $T$. The obstruction is
ghost-number: the DS BRST complex that produces $\Vir$ from
$\widehat{\mathfrak{sl}}_2$ has ghost number $1$, and every HPL
tree correction to $\Delta_z$ involves at least one ghost
propagator insertion. The ghost propagator
$h \colon F_{\gh} \to F_{\gh}[-1]$ shifts ghost number by $-1$;
the coproduct $\Delta_z \colon \cA \to \cA \otimes \cA$ has
ghost number $0$; the mismatch kills every correction. All
gravitational dynamics resides in the $A_\infty$ product
tower $\{m_k\}_{k \ge 2}$ and the collision residue $r(z)$;
the coalgebra direction is trivial.

\subsection*{12.10.\enspace The M2 brane example}

First genuinely interacting holographic example: boundary
algebra $\cW_{1+\infty}$ (infinitely many generators), Koszul
dual dg-shifted Yangian for $\mathfrak{psl}(2|2)$, line-operator
category a quantum affine superalgebra. All three genus-$2$
shells active; the planted-forest shell receives its first
nontrivial contribution from Mok's log-FM strata.

\medskip\noindent\textbf{Physical setup.}\enspace
3d $\cN = 4$ ADHM gauge theory, $N$ M2 branes
probing $\bC^2/\bZ_k$. At large $N$, the boundary VOA is
$\cW_{1+\infty}[c]$ at $c \sim N$, with strong generators of
weights $1, 2, 3, \ldots$ and rational OPE coefficients in $N$.
The Yang $R$-matrix $R(u) = u\,I + \Psi\,P$ governs the chiral
quantum group structure with $\Psi = N$. The Miura
factorisation $T(u) = \prod_{i=1}^N (u + \Lambda_i)$ produces
the elementary symmetric generators $\psi_s = e_s(\Lambda_i)$.

\medskip\noindent\textbf{The Koszul dual.}\enspace
$\cA^!_{M2,\infty} \simeq Y^{\dg}_\hbar(\mathfrak{psl}(2|2))$.
The classical $r$-matrix $k\,\Omega_{\mathfrak{psl}(2|2)}/z$
vanishes at $k = 0$ and satisfies CYBE via the Arnold relation
on the $\mathfrak{psl}(2|2)$ Casimir. The Lie superalgebra
$\mathfrak{psl}(2|2)$ has vanishing Killing form, so the
$r$-matrix uses the non-degenerate supersymmetric bilinear form
$\mathrm{str}(XY)$. The line-operator
category is
$\cC_{M2} \simeq \Rep(U_q(\widehat{\mathfrak{psl}}(2|2)))$
with $q = e^{2\pi i/(k+2)}$.

\medskip\noindent\textbf{The datum.}\enspace
\begin{align*}
\cA &= \cA_{M2,\infty},
 & \cA^! &= Y^{\dg}_\hbar(\mathfrak{psl}(2|2)),\\
\cC &= \Rep(U_q(\widehat{\mathfrak{psl}}(2|2))),
 & r(z) &= k\,\Omega_{\mathfrak{psl}(2|2)}/z,\\
\Theta_{M2} &= \sum_\Gamma
 \tfrac{W^{\log\FM}_\Gamma}{|\Aut(\Gamma)|}\otimes\Phi^{M2}_\Gamma,
 & \nabla^{\hol}_{g,n} &= d - \mathrm{Sh}_{g,n}(\Theta_{M2}).
\end{align*}

\medskip\noindent\textbf{Shadow tower.}\enspace
Cubic nonzero (nonabelian current subalgebra);
quartic nonzero ($16/(22 + 5c(N))$); quintic
$\{\mathfrak C_{M2}, Q^{\contact}_{M2}\}_H \neq 0$; tower
infinite. At genus $2$, all three shells active; the
planted-forest shell is the first contribution from Mok's
log-FM strata to the holographic genus expansion. The quartic
contact invariant is the first obstruction to planarity: it
distinguishes the full string-theoretic amplitude from its
planar limit.

\medskip\noindent\textbf{Conformal anomaly and the $1/N$
expansion.}\enspace
The conformal anomaly of $\cW_{1+\infty}[c]$ at $c = N$ is
\[
\kappa(\cW_{1+\infty}[N])
\;=\;
N \cdot (H_\infty - 1)
\;\sim\;
N \cdot \log N.
\]
The logarithmic growth in $N$ is characteristic of the
$\cW_{1+\infty}$ tower: the harmonic sum $H_N - 1$ diverges
logarithmically as $N \to \infty$. The modular
characteristic $\kappa \sim N \log N$ controls the curvature
of the genus tower at large $N$; the $1/N$ corrections are
encoded in the quartic and higher shadow invariants.

The genus-$g$ free energy at large $N$:
$F_g(N) = \kappa(N) \cdot \lambda_g^{\FP} + O(1/N)$
\textsc{(uniform-weight; multi-weight corrections from
cross-channel)}. The leading $N \log N$ term is the planar
gravitational contribution; the subleading $O(1/N)$ terms
come from the quartic contact invariant and its descendants
in the shadow tower.

The modular Koszul datum $\cH(M2)$ packages the
complete holographic correspondence into a single MC problem.
The computation extends to $N$ M5 branes (boundary VOA is
a 6d $(2,0)$ chiral algebra), $N$ D3 branes (boundary VOA
is $\cN = 4$ SYM chiral algebra), and arbitrary 3d $\cN = 4$
gauge theories; in each case, the holographic datum $\cH(T)$
is the complete algebraic encoding.

\bigskip\noindent\emph{Summary.}\enspace Sections~1--2
constructed the bar complex from $\eta = d\log(z_1 - z_2)$ and
the Arnold relation. Sections~3--4 identified these as
projections of $\Theta_\cA \in \MC(\gAmod)$. Sections~5--6
extracted the characteristic invariants from $\Theta_\cA$ and
classified algebras by shadow depth. Section~7 ran the
machine on every standard family, reading both the geometric
face and the $E_1$ algebraic face for each family. Section~8
lifted the shadow obstruction tower into number theory.
Section~9 proved scalar saturation and the Koszulness
meta-theorem. Sections~10--11 transported the machine to
three dimensions via the Swiss-cheese operad and the modular
PVA quantisation obstruction theory. Section~12 packaged
the full holographic correspondence into a six-component
modular Koszul datum controlled by a single MC equation.


% ====================================================================
\section*{13.\quad Completion and the frontier}
% ====================================================================

The holographic datum of Section~12 packages a chiral algebra,
its Koszul dual, the line-operator category, the spectral
$R$-matrix, the universal MC element, and the shadow connection
into a single algebraic object. The frontier consists of
structural questions the packaging forces: the completed
bar-cobar problem by infinite-type algebras, the analytic
sewing problem by $g \ge 1$ curvature, the factorization
envelope problem by the passage from Lie conformal input to
modular output, and the non-principal duality problem by
Drinfeld--Sokolov reduction at arbitrary nilpotent orbits.

\subsection*{13.1.\enspace The Maurer--Cartan frontier}

\noindent\textsc{Status: master conjectures MC1 through MC4 are
proved; MC5 is partially proved, with the analytic HS-sewing package
established at all genera and the genuswise BV/BRST/bar identification
conjectural.} MC3 holds for all simple types on the
evaluation-generated core via multiplicity-free $\ell$-weights
(Theorem~\ref{thm:categorical-cg-all-types},
Corollary~\ref{cor:mc3-all-types}). The residual problem
DK-4/5 (extension beyond evaluation modules) is downstream.

\medskip\noindent\textbf{MC1} (PBW concentration). For every
standard family (Kac--Moody, Virasoro, principal $\cW_N$,
$\beta\gamma$, lattice) and every genus $g \ge 1$, the PBW
spectral sequence on the genus-$g$ bar complex has
$E_\infty^{p,q}(g) = 0$ for $q \neq 0$. Proof: genus-$0$
Koszulness gives concentration of $E_1^{p,q}(g{=}0)$; the
genus-$g$ enrichment from the Hodge bundle is
$d_0^{\mathrm{PBW}}$-exact because it arises from the regular
Eisenstein series (exact under Poincar\'e residue).
Concentration is uniform in $k$.

\medskip\noindent\textbf{MC2} (universal $\Theta_\cA$). The
bar-intrinsic construction $\Theta_\cA := D_\cA - d_0
\in \gAmod$ is automatically MC because $D_\cA^2 = 0$. Scalar
saturation universality: for every one-parameter algebraic
family $\cA_k$ with rational OPE coefficients,
$\Theta_{\cA_k} = \kappa(\cA_k)\cdot\eta_{\mathrm{univ}}
\otimes\Lambda_{\mathrm{univ}}$. Proof via Whitehead
reduction ($E_2^{p,q} = H^p(\fg; \Sym^q V) = 0$ at $p = 2$ by
Whitehead's lemma for reductive $\fg$) and algebraic
semicontinuity (the non-vanishing locus is Zariski-closed,
proper, and empty at the free-field point). Ambient
$D^2 = 0$ on the planted-forest complex follows from Mok's
normal-crossings result.

\medskip\noindent\textbf{MC3} (thick generation). On the
type-$A$ Yangian module surface, the four-package MC3 problem
reduces to a single compact/completed extension packet via
(a) chromatic filtration of $K_0$ by $q$-character support,
(b) prefundamental Clebsch--Gordan closure
$V_n \otimes L^- = \bigoplus_{j=0}^n L^-(n-2j)$ at character
level, (c) Francis--Gaitsgory pro-nilpotent completion, and
(d) the remaining DK compact/completion packet. The CG
decomposition is extended to all simple types via the
Chari--Moura multiplicity-free $\ell$-weight property,
replacing the minuscule hypothesis; the remaining post-CG
completion packets beyond type~$A$ are the downstream problem.

\medskip\noindent\textbf{MC4} (completed bar-cobar). The
strong completion-tower theorem: the strong filtration axiom
$\mu_r(F^{i_1},\ldots,F^{i_r}) \subset F^{i_1+\cdots+i_r}$
yields an automatic degree cutoff, so for fixed $N$ only
finitely many degrees contribute to $F^N$, making continuity
and Mittag-Leffler automatic. The completion closure
$\CompCl(\cF_{\mathrm{ft}})$ of complete filtered objects with
finite-type associated graded carries a quasi-inverse
bar-cobar homotopy equivalence. Key results: coefficient
stability, MC twisting closure, completed twisting
representability, and the uniform PBW bridge (MC1 implies
MC4 for all standard families).

MC4 splits into two sub-problems, both proved:
\begin{itemize}
\item \emph{MC4${}^+$} (positive towers: $\cW_{1+\infty}$,
affine Yangians, RTT algebras): solved by weight stabilisation.
\item \emph{MC4${}^0$} (resonant towers: Virasoro,
non-quadratic $\cW_N$): reduced to a finite resonance problem
by the resonance-filtered bar-cobar theorem. The resonance
rank $\rho(\cA)$ measures the depth; every positive-energy
chiral algebra has $\rho < \infty$
(Theorem~\ref{thm:platonic-completion}). The Virasoro case:
$\Vir_{26-c}$ is the depth-zero resonance shadow; the genuine
$\cW_\infty$-type dual requires the full resonance-filtered
completion.
\end{itemize}

\medskip\noindent\textbf{MC5} (genus expansion). Partially proved.
The analytic sewing package is established at all genera, together
with the algebraic genus tower. The full genuswise BV/BRST/bar
identification remains conjectural. At genus~$0$, the algebraic
BRST/bar comparison is proved
(Theorem~\ref{thm:algebraic-string-dictionary}); the tree-level
amplitude pairing is conditional on
Corollary~\ref{cor:string-amplitude-genus0}; bar-cobar inversion
$\Omega(\barB(\cA)) \xrightarrow{\sim} \cA$ is Theorem~B. At
genus~$1$, the curved bar complex with
$d_{\mathrm{fib}}^2 = \kappa\cdot\omega_1$ supplies the
one-loop package, and the complementarity splitting
$Q_1(\cA) \oplus Q_1(\cA^!) = H^*(\overline\cM_{1,n}, Z(\cA))$
is the genus-$1$ modular-invariance constraint.

At $g \ge 2$ the resolution proceeds in five steps:
\begin{enumerate}[label=(\roman*),nosep]
\item \emph{Inductive genus determination}
(Theorem~\ref{thm:inductive-genus-determination}):
$\Theta^{(g)}_\cA$ is determined by $\Theta^{(<g)}_\cA$ via
the graph-sum recursion on $\overline\cM_{g,n}$.
\item \emph{2D convergence}: no UV renormalisation on curves;
the Feynman integrals
$W_\Gamma = \int_{\sigma_\Gamma}\omega_\Gamma$ converge
absolutely on each stratum without counterterm subtraction.
\item \emph{Analytic-algebraic comparison}
$D^{\mathrm{an}} = D^{\mathrm{alg}}$ on the algebraic core.
\item \emph{General HS-sewing}
(Theorem~\ref{thm:general-hs-sewing}): polynomial OPE growth
plus subexponential sector growth implies the
Hilbert--Schmidt sewing condition, yielding trace-class closed
amplitudes at every genus.
\item \emph{Heisenberg one-particle sewing} identifies the
Heisenberg sewing amplitude with a Fredholm determinant,
supplying the decisive first-case verification.
\end{enumerate}

At multi-weight $g \ge 2$ (all-weight), the genus expansion
admits an explicit cross-channel correction:
$F_g(\cA) = \kappa(\cA)\cdot\lambda_g^{\FP} + \delta F_g^{\cross}$,
proved for $\cW_3$ by graph-by-graph computation over all seven
stable graphs at $g = 2$ and all forty-two stable graphs at
$g = 3$. The scalar formula of the uniform-weight expansion
\emph{fails} for multi-weight algebras at $g \ge 2$
(resolving Open Problem~\ref{op:multi-generator-universality}
negatively). A universal closed form for the gravitational
cross-channel correction covers principal $\cW_N$:
$\delta F_2^{\grav}(\cW_N, c)
= (N-2)(N+3)/96 + (N-2)(3N^3 + 14N^2 + 22N + 33)/(24c)$,
exact for $\cW_3$ and a lower bound for $N \ge 4$. The
correct receptacle at $g \ge 1$ remains the coderived category:
curvature forces coderived/contraderived passage.

\medskip\noindent\textbf{Completion programme: $q$-windows and
completion entropy.} The bar-cobar quasi-isomorphism
$\Omega(\barB(\cA)) \xrightarrow{\sim} \cA$ is proved at each
finite-type stage $\cW_N$. The passage to the inverse limit
$\cW_\infty = \varprojlim \cW_N$ requires completed bar-cobar;
the strong filtration axiom gives a quotientwise-finite
differential. The completed bar complex decomposes into finite
windows indexed by reduced weight $\rho(a) = \mathrm{wt}(a) - 1$.

For Virasoro at $q = 2$: the window $K_2(\Vir)$ has basis
$\{sT, sT|sT\}$, and the bar differential on the two-dimensional
complex is $d(sT|sT) = s(T\cdot T)$. The product $T\cdot T$
decomposes into the quasi-primary $\Lambda$ (weight $4$,
reduced weight $3 > 2$, projects to zero), $\partial^2 T$
(reduced weight $3 > 2$, projects to zero), and the central
term $(c/2)\cdot\mathbf 1$. Only the central term survives:
\[
d(sT|sT)|_{K_2} \;=\; (c/2)\cdot s\mathbf 1.
\]
The modular characteristic $\kappa(\Vir_c) = c/2$ is the sole
surviving coefficient of the bar differential on the smallest
nontrivial window.

Window dimensions grow exponentially. Define the completion
entropy $h_K(\cA) := \log(\rho_\cA^{-1})$, with $\rho_\cA$ the
radius of convergence of the primitive generating series from
the vacuum character. The entropy measures kinematic
completion complexity and forms a monotone ladder
\[
h_K(\cW_2) \approx 0.567
< h_K(\cW_3) \approx 0.772
< h_K(\cW_4) \approx 0.835
< \cdots
< h_K(\cW_\infty) \approx 0.872,
\]
governed at the limit by the MacMahon plane-partition
generating function
$\chi_{\cW_\infty}(q) = \prod_{n \ge 2}(1 - q^n)^{-(n-1)}$.

\subsection*{13.2.\enspace The analytic frontier}

Curvature forces this direction. At $g \ge 1$ the bar complex
satisfies $d_{\mathrm{fib}}^2 = \kappa\cdot\omega_g \neq 0$;
the ordinary derived category is empty, and the correct
receptacle is the coderived category, requiring
Hilbert-space-valued structures.

The bare VOA is a dense algebraic skeleton; the object for
partition functions is the sewing envelope $\cA^{\mathrm{sew}}$,
the Hausdorff completion in the topology of all-amplitude
seminorms $\|a\|_{\mathrm{amp}} := \sup_{v \in \cV}
\langle v, \pi(a) v\rangle$. The HS-sewing condition:
\[
\sum_{a,b,c \ge 0} q^{a+b+c}\|m^c_{a,b}\|^2_{\mathrm{HS}}
\;<\;\infty
\]
for $|q| < 1$ implies closed amplitudes
$\Tr(\pi(a)\cdot q^{L_0})$ are trace-class and the sewing
operation converges absolutely. An analytic Koszul pair is
one for which the analytic bar-cobar adjunction restricts to a
Quillen equivalence on sewing-complete categories.

Four targets (two proved, two conjectural):
\begin{enumerate}[label=(\alph*),nosep]
\item \emph{Heisenberg sewing} (decisive first case, proved):
sewing envelope of $\cH_k$ is
$\Sym\,A_2(D) \cong \mathrm{ind\text{-}Hilb}(\cH_k)$
(Moriwaki 2026).
\item \emph{Lattice sewing} (proved): sewing envelope of
$V_\Lambda$ is vertex-algebraic completion by lattice theta
functions.
\item \emph{Analytic realisation criterion} (conjectural):
HS-sewing on $\cA$ plus dual HS on $\cA^!$ should suffice.
\item \emph{Boundary bar duality} (conjectural):
$B^{\mathrm{an}}(\cA_\partial) \simeq
B^{\mathrm{top}}(\mathrm{Fact}^{\mathrm{bulk}}_T)$.
\end{enumerate}

\subsection*{13.3.\enspace Factorization envelopes and the modular Koszul datum}

The bar construction starts from a chiral algebra, but the
natural input in most geometric constructions is a Lie conformal
algebra. The factorisation envelope is the functor producing a
chiral algebra from Lie conformal data; the programme asks
whether the entire modular Koszul package can be constructed
functorially at the Lie conformal level, without passing
through the vertex algebra. The target is a universal modular
factorization envelope $U^{\mod}_X(L)$, left adjoint to
extracting primitive currents.

A cyclically admissible Lie conformal algebra $L$ (conformal
grading, compatible decreasing filtration, bounded poles,
invariant bilinear pairing) produces the modular Koszul datum
\[
\Pi_X(L)
\;=\;
\bigl(
\mathrm{Fact}_X(L),\;
\bar B_X(L),\;
\Theta_L,\;
\cL_L,\;
(V^{\mathrm{br}}_L, T^{\mathrm{br}}_L),\;
R_4^{\mod}(L)
\bigr),
\]
with each component functorial in $L$. The target universal
envelope $U^{\mod}_X(L)$ satisfies the adjunction
\[
\Hom_{\mathsf{Fact}^{\mod}}(U^{\mod}_X(L), \cF)
\;\cong\;
\Hom_{\mathsf{LCA}^{\cyc}}(L, \mathrm{Prim}^{\mod}(\cF)),
\]
and $\Theta_L = \Theta^{\mathrm{env}}_{\le\infty}(L)$ is the
universal MC class. Direct sums: $\kappa$, $T^{\mathrm{br}}$,
$\Delta$, $R_4^{\mod}$ decompose additively. BRST reduction:
$\Theta_{\cW_N} = H^0_{Q_{\DS}}(\Theta_{V_k(\fg)\otimes F_{\gh}})$,
the shadow tower of the $W$-algebra is the DS reduction of
the full current-plus-ghost tower, not of the bare affine tower.

\subsection*{13.4.\enspace Non-principal $W$-algebra duality}

Drinfeld--Sokolov reduction connects affine landscape to
$W$-algebra landscape. For principal $f$, the reduction commutes
with bar-cobar duality by Feigin--Frenkel, and the holographic
datum descends. For non-principal $f$, this commutation is
unproved. The theory demands the extension: non-principal
$\cW$-algebras include the physically central cases
($\cW_k(\mathfrak{sl}_N, f_{\mathrm{sub}})$ controls $\cN = 2$
superconformal theories) and the mathematically central ones
(Feigin--Tipunin at admissible levels).

The hook-type nilpotent orbit in type $A$ is the first
non-principal corridor, conditional on DS-bar compatibility
(Theorem~\ref{thm:hook-transport-corridor}). For a partition
$\lambda = (n - p, 1^p)$ in $\mathfrak{sl}_N$,
\[
(\cW_k(\mathfrak{sl}_N, f_\lambda))^!
\;\simeq\;
\cW_{k^\vee_\lambda}(\mathfrak{sl}_N, f_{\lambda^t}),
\]
where $\lambda^t$ is the transpose and $k^\vee_\lambda$ is a
rational function of $k$. Proof: for hook-type partitions, DS
commutes with bar-cobar by Fehily and
Creutzig--Linshaw--Nakatsuka--Sato (2023--2025).

The transport propagation lemma: hook-type seeds combined with
edge-compatibility propagate duality results along edges of
the nilpotent Hasse diagram in type~$A$. The type-$A$
transport-to-transpose conjecture: for every partition
$\lambda$ of $N$, the duality formula holds. The general
obstruction is proving that DS reduction commutes with
bar-cobar at the chain level, i.e.\ that the natural map
$\mathrm{DS}(\barB(\widehat\fg_k)) \to
\barB(\mathrm{DS}(\widehat\fg_k))$ is a quasi-isomorphism.

\subsection*{13.5.\enspace The boxed machine}

\[
\boxed{
\text{homotopy chiral input }\cA
\;+\;
\text{log-FM cutting cooperad }\cC^!_{\ch}
\;+\;
\text{modular convolution }L_\infty
\;\;\Longrightarrow\;\;
\Theta_\cA,\;
\cT^{\mod}_{\Theta_\cA},\;
\kappa,\;
\Delta_\cA,\;
\mathfrak R^{\mod}_4,\;\ldots
}
\]

The modular convolution $L_\infty$-algebra $\gAmod$ is the
single organising structure. It carries a natural modular
$L_\infty$ structure from the Feynman transform of the modular
operad; $\Conv_{\mathrm{str}}(\cC^!_{\ch}, \cP^{\ch})$ is its
strict model. The universal MC element
$\Theta_\cA \in \MC(\gAmod)$ is proved: it is the bar-intrinsic
extraction $\Theta_\cA := D_\cA - d_0$, automatically MC because
$D_\cA^2 = 0$.

The shadow obstruction tower consists of finite-order
projections:
\begin{align*}
\Theta_\cA^{\le 2}&:\qquad\kappa(\cA)
 &&\text{(modular characteristic, scalar curvature)},\\
\Theta_\cA^{\le 3}&:\qquad\mathfrak C(\cA)
 &&\text{(cubic shadow, Lie structure)},\\
\Theta_\cA^{\le 4}&:\qquad\mathfrak Q(\cA)
 &&\text{(quartic resonance class, contact)},\\
\Theta_\cA^{\le r}&:\qquad\mathrm{Sh}_r(\cA)
 &&\text{(degree-$r$ shadow)},\\
\Theta_\cA&:\qquad\varprojlim_r\Theta_\cA^{\le r}
 &&\text{(universal MC element)}.
\end{align*}
Theorems~A--D and Theorem~H are proved projections at the
scalar level $\kappa$. The holographic datum
$\cH(T) = (\cA, \cA^!, \cC, r(z), \Theta_\cA, \nabla^{\hol})$
packages $\Theta_\cA$ and its projections into the data of a
3d HT field theory.

\begin{principle}[The four-test interface]
\label{princ:four-test-interface}
\index{four-test interface|textbf}%
The modular Koszul machine has a complete algebraic-geometric
interface with $\overline\cM_{g,n}$ consisting of four
independent proved tests:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item $D_\cA^2 = 0$: the bar differential squares to zero at
all genera and degrees (Theorems~\ref{thm:bar-modular-operad},
\ref{thm:quantum-diff-squares-zero}).
\item $\mathrm{obs}_1(\cA) = \kappa(\cA)\cdot\lambda_1$
unconditionally at genus~$1$ for all families;
$\mathrm{obs}_g(\cA) = \kappa(\cA)\cdot\lambda_g$ for
uniform-weight algebras at all genera via clutching/GRR;
for multi-weight algebras at $g \ge 2$ (all-weight), with
cross-channel
correction $\delta F_g^{\cross}$
(Theorem~\ref{thm:modular-characteristic},
Theorem~\ref{thm:multi-weight-genus-expansion}).
\item $Q_g(\cA) + Q_g(\cA^!) = H^*(\overline\cM_g, Z(\cA))$:
complementarity assembles the Koszul pair into a Lagrangian
decomposition
(Theorem~\ref{thm:quantum-complementarity-main}).
\item Sewing: genus-$g$ amplitudes converge from lower-genus
data (Theorem~\ref{thm:general-hs-sewing}).
\end{enumerate}
Each test captures a distinct aspect: (i)~is purely algebraic
and requires no Koszulness; (ii)~identifies the tautological
class but does not involve $\cA^!$; (iii)~requires the Koszul
pair but is genus-by-genus; (iv)~is analytic and independent
of the Hodge-class identification. Any three can hold with
the fourth failing. Three regions lie outside: multi-weight
at $g \ge 2$ (all-weight, resolved with cross-channel
correction, Open
Problem~\ref{op:multi-generator-universality}), BV/BRST${}={}$bar
at higher genus (Conjecture~\ref{conj:master-bv-brst}), and
non-perturbative completion.
\end{principle}

\medskip\noindent\textbf{The holographic frontier.} The
holographic datum $\cH(T)$ is a boundary object. Its lift to a
genuine 3d bulk theory is controlled by the relative
holographic deformation complex
$\fh_T^\Theta := \fib(\fg_T^{\SC} \to \gAmod)_{\alpha_T}$:
lifts of $\Theta_\cA$ are MC elements of the twisted fibre.
The graded obstruction tower
$[\fo_r(\beta)] \in H^2(\gr^F_r \fh_T^\Theta)$
turns the frontier into cohomology calculus. At depth~$4$,
the relative quartic obstruction
$\mathfrak R_4^{\mathrm{rel}}(T)$ is the first invariant
detecting when a boundary datum cannot arise from a planar
holographic realisation. The Loop--Connes principle
$\beta_{\der}^*(\Delta_{\mathrm{open}}) = \Lambda_P$:
closed genus creation is the image of the open BV operator
under the derived-centre map; loops in the bulk are traces on
the boundary.

\medskip\noindent\textbf{Cyclic trace, ribbon structure, and $1/N$.}
A bare modular graph sum does not define a literal 't~Hooft
expansion (Lemma~\ref{lem:bare-graph-no-thooft}). Cyclic trace
structure on the open $E_1$-chiral algebra resolves this:
cyclicity enables ribbon thickening
(Theorem~\ref{thm:cyclicity-ribbon}), and a matrix realisation
gives the exact weight $N^{\chi(\Sigma_\Gamma)}$
(Theorem~\ref{thm:exact-n-chi-weighting}). The three levels of
language (plain modular $E_1$ genus expansion, cyclic traced
modular $E_1$ 't~Hooft expansion, ribbonised modular
Swiss-cheese holographic 't~Hooft language) are made precise
in the $E_1$ modular Koszul chapter
(Chapter~\ref{chap:e1-modular-koszul}).

\subsection*{13.6.\enspace Admissible levels and logarithmic CFT}

At admissible levels $k = -h^\vee + p/q$ (coprime $p \ge h^\vee$,
$q \ge 1$), the Zhu algebra $A(\cV_k(\fg))$ is semisimple but
the vertex algebra is not simple: there is a maximal proper
ideal $J_k$ with $L_k(\fg) = \cV_k(\fg)/J_k$. The bar complex
of $\cV_k$ acquires a periodic CDG structure indexed by $q$-th
roots of unity: the curvature $m_0 = \kappa\cdot\omega_g$ factors
through $\Phi_q(\zeta)$, and the weight filtration has a finite
plateau at level $N = q$. This is the algebraic door to
logarithmic CFT on the degenerate admissible lane. On the
non-degenerate admissible lane the simple quotient is rational;
on the degenerate lane the simple quotient has a logarithmic
module category. Weightwise finite-page character degeneration
holds on the non-degenerate lane; identification of the
resulting bar cohomology with logarithmic extensions is not
proved here.

\subsection*{13.7.\enspace Relative Feynman transform}

The modular bar coalgebra $\barB_{\mod}(\cA)$ is an algebra
over the relative Feynman transform
$\mathrm{FT}_{\mathsf{Com}_{\mod}/\SCchtop}$, the algebraic
skeleton shared by the factorisation approach (\S10.8) and the
operadic approach. Factorisation on
$\Ran(\Sigma_g)\times\Ran(\bR)$ over $\overline\cM_g$ produces
it via families of factorisable $\cD$-modules; the operadic
structure on $\SCchtop_{\mod}$ produces it via formal
completion.

\emph{Recognition.} The tree-level part $D_0$ is the
$E_1$ coassociative coalgebra structure (encoding boundary
$A_\infty$ data); the genus-raising part $D_1$
is the $\mathsf{Com}_{\mod}$-modular structure.
The $\SCchtop$ datum is the pair
$\bigl(C^\bullet_{\mathrm{ch}}(\cA,\cA),\,\cA\bigr)$
of chiral derived center and boundary algebra.

\subsection*{13.8.\enspace The Calabi--Yau quantum group programme (Volume III)}

Volume~III constructs the concrete examples of $E_1$-chiral
quantum groups from Calabi--Yau geometry. The abstract framework
of Sections~1--9 receives its geometric instantiation: the CY
categories produce chiral algebras via a functor
$\Phi \colon \mathrm{CY}_d\text{-}\mathrm{Cat} \to
E_2\text{-}\mathrm{ChirAlg}$, and the resulting chiral algebras
carry the full modular Koszul package.

\medskip\noindent\textbf{The CY-to-chiral functor.}\enspace
For a CY$_d$ category $\cC$ (a smooth proper dg-category with
$d$-Calabi--Yau structure), the functor $\Phi$ produces an
$E_2$-chiral algebra $\Phi(\cC)$ whose:
\begin{itemize}[nosep]
\item central charge is $\kappa_{\ch}(\Phi(\cC))$, a function of
the CY structure (for local surfaces $\mathrm{Tot}(K_S \to S)$:
$\kappa_{\ch} = \chi(S)/2$, where $\chi$ is the topological Euler
characteristic);
\item $r$-matrix is the collision residue of the CY-derived MC
element, carrying the BPS state structure of the CY geometry;
\item shadow tower identifies with the automorphic correction of
the associated BKM superalgebra (when one exists).
\end{itemize}
The functor is proved for $d = 2$ (CY$_2$ = K3 and abelian
surfaces) and for $d = 3$ ($\infty$-categorical proof:
$\mathrm{HH}^{-2}_{E_1} = 0$ implies the $E_3$-lifting is
contractible).

\medskip\noindent\textbf{Example: $K3 \times E$.}\enspace
The product of a K3 surface and an elliptic curve is a CY$_3$
with $\kappa_{\ch} = \chi(K3)/2 = 12$ (since $\chi(K3) = 24$).
The BKM superalgebra is the Borcherds--Kac--Moody algebra
$\fg_{\Phi_{10}}$ with root multiplicities encoded by the Igusa
cusp form $\Phi_{10}$, weight $10 = 2\kappa_{\mathrm{BKM}}$
with $\kappa_{\mathrm{BKM}} = 5$. The Koszul conductor:
$K = 0$ (free-field branch, CY complementarity).

The shadow tower of $\Phi(K3 \times E)$ identifies with the
automorphic correction: the coefficients
$\mathrm{Sh}_r(\Phi(K3 \times E))$ are the Taylor coefficients
of $\log \Phi_{10}$ expanded in the appropriate Siegel modular
coordinates. The shadow-Siegel gap (the discrepancy between the
shadow tower and the full Siegel modular form) measures the
genuinely genus-$2$ information invisible to the shadow tower.

\medskip\noindent\textbf{Example: conifold.}\enspace
The resolved conifold $\mathrm{Tot}(\cO(-1)^{\oplus 2} \to
\bP^1)$ is a toric CY$_3$ with $\kappa_{\ch} = 1$ (from
DT computation; the formula $\kappa_{\ch} = \chi(S)/2$ applied
to the base $\bP^1$ gives $\chi(\bP^1)/2 = 1$, which is
numerically correct but the derivation requires care since
$\cO(-1)^{\oplus 2} \neq K_{\bP^1}$). The CoHA
(cohomological Hall algebra) of the conifold quiver
$Q = \bullet \rightrightarrows \bullet$ carries the $E_1$-chiral
quantum group structure; integrality of the DT invariants
$\Omega(\gamma) \in \bZ$ is encoded in the CoHA product.

\medskip\noindent\textbf{Example: $\bC^3$.}\enspace
The simplest non-compact CY$_3$. The shadow tower at
$\kappa_{\ch} = \Psi$ (the deformation parameter of
$\cW_{1+\infty}$) produces the perturbative constant-map
Gromov--Witten free energies $F_g^{\mathrm{GW,const}}(\bC^3)$.
On the DT side, the MacMahon function
$M(q) = \prod_{n \ge 1}(1 - q^n)^{-n}$ counts plane partitions.
The shadow IS the full GW answer for $\bC^3$ because there are
no compact curves (no worldsheet instantons); the two towers
(shadow and GW) agree exactly.

\subsection*{13.9.\enspace The 6d holomorphic Chern--Simons hierarchy}

The primary geometric source of $E_1$-chiral quantum groups is
6d holomorphic Chern--Simons theory on a Calabi--Yau threefold
$Y$. The hierarchy of theories descends by dimensional reduction
and defect insertion:

\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{llll}
\textbf{Theory} & \textbf{Space} & \textbf{Output} & \textbf{Status}\\ \hline
6d hCS & $Y$ (CY$_3$) & BPS/CoHA algebra & source\\
5d CS & $\bR \times S$ (CY$_2$) & affine Yangian & reduction\\
4d CS & $\Sigma \times C$ & integrable system & proved\\
3d HT CS & $\bR \times C$ & boundary $+$ bulk & proved\\
2d chiral & $C$ & bar complex & proved
\end{tabular}
\end{center}

\noindent
Each step in the hierarchy corresponds to a dimensional reduction
or defect insertion, and the modular Koszul datum descends
functorially through each step. The bar complex of the 2d chiral
algebra on $C$ is the terminal output; the 6d theory on $Y$ is the
geometric origin. The shadow tower of the 2d chiral algebra
encodes the BPS state content of the 6d theory through the
automorphic correction.

\medskip\noindent\textbf{Codimension-$2$ defects.}\enspace
For a holomorphic curve $C \subset Y$ (a codimension-$2$ defect),
the boundary algebra restricted to the defect is
$\cW_{1+\infty}$ at $\Psi = -\sigma_2(N_{C/Y})$, where
$\sigma_2$ is the second Chern root of the normal bundle
$N_{C/Y}$. For $C = \bP^1 \subset \bC^3$ with
$N_{C/\bC^3} = \cO(-1)^{\oplus 2}$: $\sigma_2 = 1$, giving
$\Psi = -1$ and $c = 1$ from the Sugawara construction.
The spectral parameters of the chiral quantum group come from the
two independent directions in $N_{C/Y}$.

\medskip\noindent\textbf{The Drinfeld centre closes the
circle.}\enspace
The $E_n$ operadic circle
\[
E_3(\text{bulk})
\;\to\;
E_2(\text{boundary chiral})
\;\to\;
E_1(\text{bar/QG})
\;\to\;
E_2(\text{Drinfeld centre})
\;\to\;
E_3(\text{derived centre})
\]
is the holographic structure of the programme. Each arrow is:
restriction to codimension-$2$ defect, ordered bar complex,
categorified averaging (Drinfeld centre), and higher Deligne
(derived centre). The circle closes for 3d HT theories with
conformal vector: the Drinfeld centre
$\cZ(\Rep^{E_1}(Y^+(\widehat{\fg\fl}_1)))
\cong \Rep^{E_2}(\cW_{1+\infty})$
identifies the $E_2$ Drinfeld centre of the $E_1$ quantum group
representation category with the $E_2$ representation category of
the boundary chiral algebra. This is the categorical level of
the holographic correspondence.

\subsection*{13.10.\enspace The ten deepest open problems}

The programme has been attacked by 732 adversarial agents and
survived. The surviving frontier, ranked by structural depth:

\begin{enumerate}[nosep]
\item \emph{Closing the $E_n$ circle}
 (Conjecture~\ref{conj:v1-drinfeld-center-equals-bulk}):
 $\cZ(\mathbf U_\cA) \simeq
 \cZ^{\der}_{\ch}(\cA)$. Three obstructions identified.
\item \emph{Drinfeld double at $E_1$-chiral level}: construct
 $\cA \bowtie \cA^!$ as Hopf; identify antipode with
 orientation reversal.
\item \emph{Chain-level BV${}={}$bar for class~M}: coderived
 proved; chain-level false at genus~$1$.
\item \emph{A genuinely new $E_1$ invariant}: a number from
 $E_1$ theory that $E_\infty$ cannot compute.
\item \emph{Equivalence of five $E_1$-chiral notions}: Notions
 A--E may define different categories.
\item \emph{Chiral $R$-matrices controlling holomorphic Wilson
 lines}: braiding of ordered conformal blocks.
\item \emph{CY-A at $d = 3$}: now proved ($\infty$-categorical,
 $\mathrm{HH}^{-2}_{E_1} = 0$). Removed from open problems.
\item \emph{6d hCS defect algebra in full generality}: link
 algebra on $S^3$ from CY$_2$ normal fiber.
\item \emph{$E_1$ Verlinde formula}: non-commutative fusion
 using the $R$-matrix.
\item \emph{BKM denominator $=$ bar Euler product}: chain-level
 root multiplicities from BPS degeneracies.
\end{enumerate}

\emph{Homotopy-involutivity.}
$\mathrm{FT}_{\mathsf{Com}_{\mod}/\SCchtop}^{\;2} \simeq \id$.
Genus-$0$ involutivity from operadic homotopy-Koszulity;
closed-colour modular involutivity from the Feynman involution
(Theorem~\ref{thm:feynman-involution}); assembly via the
genus-filtration spectral sequence.

\emph{Three routes unified.} Route~B (factorisation) is global
truth; Route~A (operadic) is local approximation; Route~C
(this section) is the categorical image. The factorisation
structure projects to the relative Feynman transform by
forgetting $\cD$-module data; the operadic structure injects
by formal completion.

\subsection*{13.11.\enspace Computational infrastructure}

Every formula has been verified by an independent symbolic
computation layer comprising tens of thousands of tests across
several hundred modules, covering the shadow obstruction tower
through degree $32$, the standard landscape for all seven
families, the genus-$2$ and genus-$3$ planted-forest formulas,
the DS-shadow cascade (degrees $2$--$8$ for $N = 2, \ldots, 5$),
the $\cW_3$ multi-generator shadow metric, the B\"ocherer bridge
at genus~$2$, the Pixton shadow bridge, the entanglement
programme, the non-simply-laced bar computations ($B_2$, $C_2$,
$G_2$, $F_4$), minimal model bar and fusion rules, the dressed
propagator engine (scalar complementarity, $R$-matrix
$R_1 = 1/12$), and the constrained Epstein zeta. The
computation is adversarial: tests encode cross-family
consistency checks that cannot be fooled by hardcoded values.

Volume~III extends the engine to Calabi--Yau geometry: forty-two
CY/BKM compute engines with $5700+$ tests cover the
$K3 \times E$ programme (shadow-Siegel gap, BKM root
multiplicities, moonshine multiplier, Schottky barrier), toric
CY$_3$ CoHA integrality, and the automorphic correction as
shadow obstruction tower identification.

Volume~II develops the 3d theory in three new chapters: the
factorisation Swiss-cheese algebra (global truth on
$\Ran(\Sigma_g)\times\Ran(\bR)$), the modular Swiss-cheese
operad (local approximation), and the relative Feynman
transform (algebraic skeleton). Together with the 3d gravity
chapter, the affine half-space BV theorem, and eleven
additional computational engines, these constitute the
Volume~II programme.

\subsection*{13.12.\enspace The single open problem}

Everything proved in this monograph is a finite-order projection
of the universal MC element
$\Theta_\cA \in \MC(\gAmod)$. Everything open is a question
about its ambient:

\begin{center}
\fbox{\parbox{0.85\textwidth}{\centering
\emph{Characterise the modular convolution algebra $\gAmod$
as a geometric object.}
}}
\end{center}

\noindent
Precisely: the modular convolution algebra is the endomorphism
algebra of the Lagrangian embedding
$\cL_\cA \hookrightarrow \cM_{\mathrm{vac}}(\cA)$ in the
$(-2)$-shifted symplectic stack of vacua. Volume~I computes
the Taylor jets of this embedding (the shadow obstruction
tower). Volume~II identifies the local composition law (the
Swiss-cheese operad). What remains is the global geometry of
the stack itself: the derived symplectic structure, the moduli
of Lagrangians, and the higher-categorical descent that would
make the construction independent of choices.

The approximately $150$ open conjectures in these volumes are
projections of this single question:
\begin{itemize}[nosep]
\item the $\cD$-module purity conjecture asks whether the
Lagrangian is pure (characterisation~(xii) of Koszulness);
\item the non-principal $W$-duality programme asks how the
Lagrangian transforms under DS reduction at arbitrary nilpotent
orbits;
\item the analytic completion programme asks when the algebraic
Lagrangian extends to a convergent one (the sewing envelope);
\item the factorization envelope programme asks for the universal
construction of the Lagrangian from Lie conformal data alone;
\item the holographic completion question asks whether the
genus-$0$ Lagrangian extends over $\overline\cM_{g,n}$;
\item the Calabi--Yau quantum group programme (Volume~III):
Sections~1--9 introduce $E_1$-chiral quantum groups as abstract
algebraic-geometric objects; Volume~III constructs the concrete
examples from CY geometry. The functor
$\Phi \colon \mathrm{CY}_d\text{-}\mathrm{Cat} \to
E_2\text{-}\mathrm{ChirAlg}$ produces chiral algebras from CY
categories (proved for $d = 2$ and $d = 3$; the $d = 3$ proof
uses the $\infty$-categorical vanishing
$\mathrm{HH}^{-2}_{E_1} = 0$). The CY quantum groups
(CoHA, quantum toroidal algebras, BPS algebras) are the flesh
on the algebraic skeleton of Sections~1--9. The theories
studied include 6d holomorphic Chern--Simons on CY$_3$ (the
primary source), 4d and~5d HT Chern--Simons, 6d little string
theory, and M5 brane theory. The shadow tower of the CY chiral
algebra IS the automorphic correction of the BKM superalgebra;
at $\kappa_{\mathrm{ch}} = \Psi$ the shadow produces the
constant-map Gromov--Witten free energies of $\bC^3$. The
Drinfeld centre
$\cZ(\Rep^{E_1}(Y^+(\widehat{\mathfrak{gl}}_1)))
\cong \Rep^{E_2}(\cW_{1+\infty})$ closes the
$E_n$ operadic circle.
\end{itemize}
Each is a different facet of the geometry of $\gAmod$, and
none requires going beyond the framework already established.

\bigskip

\noindent
The entire structure unfolds from a single datum: the
logarithmic $1$-form $\eta = d\log(z_1 - z_2)$. At $n$ points
it became a differential on the Fulton--MacPherson
compactification; across all genera it became the total bar
differential $D_\cA$; in the modular convolution algebra it
became the Maurer--Cartan element $\Theta_\cA = D_\cA - d_0$.
One $1$-form, one relation (Arnold), one extraction (residues),
one ordering (the real line): a universal invariant of chiral
algebras that is algebraic, computable, and complete.

Volume~I constructs $E_n$-chiral algebras as
algebraic-geometric objects on curves and their configuration
spaces: factorisation algebras, bar complexes on every curve
geometry, $R$-matrices, derived chiral centres with
$E_2$/$E_3$ structure, the $\SCchtop$ datum on the derived
centre pair. Volume~II interprets these constructions
physically: the derived centre IS the bulk of a 3d gauge
theory; 3d quantum gravity is the climax. Volume~III
constructs the concrete CY quantum groups from
higher-dimensional HT theories: the
$E_1$-chiral quantum groups that Volume~I introduced abstractly
receive their geometric instantiation. Together: holomorphic
chiral factorisation (co)homology via bar and cobar chain
constructions at various geometric locations, and the different
locations produce the different operads at play.

\begin{thebibliography}{99}

\bibitem{BD04}
A.~Beilinson and V.~Drinfeld,
\textit{Chiral Algebras},
AMS Colloquium Publications, vol.~51,
American Mathematical Society, Providence, RI, 2004.

\bibitem{BGS96}
A.~Beilinson, V.~Ginzburg, and W.~Soergel,
Koszul duality patterns in representation theory,
\textit{J.~Amer.\ Math.\ Soc.}~\textbf{9} (1996), 473--527.

\bibitem{BS88}
A.~Beilinson and V.~Schechtman,
Determinant bundles and Virasoro algebras,
\textit{Comm.\ Math.\ Phys.}~\textbf{118} (1988), 651--701.

\bibitem{CG17}
K.~Costello and O.~Gwilliam,
\textit{Factorization Algebras in Quantum Field Theory},
vols.~1--2, Cambridge University Press, 2017/2021.

\bibitem{DS85}
V.~Drinfeld and V.~Sokolov,
Lie algebras and equations of Korteweg--de Vries type,
\textit{J.~Soviet Math.}~\textbf{30} (1985), 1975--2036.

\bibitem{FG12}
J.~Francis and D.~Gaitsgory,
Chiral Koszul duality,
\textit{Selecta Math.\ (N.S.)}~\textbf{18} (2012), 27--87.

\bibitem{FP00}
C.~Faber and R.~Pandharipande,
Hodge integrals and moduli spaces of curves,
in \textit{Moduli of Curves and Abelian Varieties},
Aspects Math.~E33, Vieweg, 2000, pp.~109--130.

\bibitem{GeK98}
E.~Getzler and M.~Kapranov,
Modular operads,
\textit{Compositio Math.}~\textbf{110} (1998), 65--126.

\bibitem{FF90}
B.~Feigin and E.~Frenkel,
Quantization of the Drinfeld--Sokolov reduction,
\textit{Phys.\ Lett.\ B}~\textbf{246} (1990), 75--81.

\bibitem{FlajoletSedgewick}
P.~Flajolet and R.~Sedgewick,
\textit{Analytic Combinatorics},
Cambridge University Press, 2009.

\bibitem{KM94}
M.~Kontsevich and Yu.~Manin,
Gromov--Witten classes, quantum cohomology, and enumerative geometry,
\textit{Comm.\ Math.\ Phys.}~\textbf{164} (1994), 525--562.

\bibitem{Kontsevich03}
M.~Kontsevich,
Deformation quantization of Poisson manifolds,
\textit{Lett.\ Math.\ Phys.}~\textbf{66} (2003), 157--216.

\bibitem{KRW03}
V.~Kac, S.-S.~Roan, and M.~Wakimoto,
Quantum reduction for affine superalgebras,
\textit{Comm.\ Math.\ Phys.}~\textbf{241} (2003), 307--342.

\bibitem{LV12}
J.-L.~Loday and B.~Vallette,
\textit{Algebraic Operads},
Grundlehren der Mathematischen Wissenschaften, vol.~346,
Springer, Berlin, 2012.

\bibitem{Mumford83}
D.~Mumford,
Towards an enumerative geometry of the moduli space of curves,
in \textit{Arithmetic and Geometry, Vol.~II},
Progr.\ Math., vol.~36, Birkh\"auser, 1983, pp.~271--328.

\bibitem{Priddy70}
S.~Priddy,
Koszul resolutions,
\textit{Trans.\ Amer.\ Math.\ Soc.}~\textbf{152} (1970), 39--60.

\bibitem{EK00}
P.~Etingof and D.~Kazhdan,
Quantization of Lie bialgebras V: quantum vertex operator algebras,
\textit{Selecta Math.\ (N.S.)}~\textbf{6} (2000), 105--130.

\bibitem{Mok25}
C.-P.~Mok,
\emph{Logarithmic Fulton--MacPherson configuration spaces},
arXiv:2503.17563, 2025.

\bibitem{MS24}
A.~Moreno and P.~Safronov,
Chiral Koszul duality on moduli of curves,
preprint, 2024.

\bibitem{RNW19}
N.~Rozenblyum, S.~Nagy, and D.~Wagner,
Convolution $L_\infty$-algebras and Maurer--Cartan,
preprint, 2019.

\bibitem{LorgatVirR}
R.~Lorgat,
\textit{The Virasoro spectral $R$-matrix: closed form and non-formality},
preprint, 2026.

\bibitem{LorgatSevenFaces}
R.~Lorgat,
\textit{The seven faces of the collision residue},
preprint, 2026.

\end{thebibliography}

\end{document}
