\documentclass[11pt]{article}

% ================================================================
% Packages
% ================================================================
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathrsfs}
\usepackage[shortlabels]{enumitem}
\usepackage{booktabs}
\usepackage{array}
\usepackage{microtype}
\usepackage[colorlinks=true,linkcolor=blue!60!black,
 citecolor=green!40!black,urlcolor=blue!60!black]{hyperref}

% ================================================================
% Theorem environments
% ================================================================
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{computation}[theorem]{Computation}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% ================================================================
% Macros
% ================================================================
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\barB}{\bar{B}}
\newcommand{\fg}{\mathfrak{g}}
\newcommand{\fsl}{\mathfrak{sl}}
\newcommand{\Walg}{\mathcal{W}}
\newcommand{\Vir}{\mathrm{Vir}}
\newcommand{\Res}{\operatorname{Res}}
\newcommand{\Sh}{\mathrm{Sh}}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\DS}{\mathrm{DS}}
\newcommand{\Convstr}{\mathrm{Conv}_{\mathrm{str}}}

\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\tr}{tr}

\numberwithin{equation}{section}

% ================================================================
\begin{document}

\title{The first rank-2 holographic modular Koszul datum:\\
$H(\Walg_3)$}

\author{Raeez Lorgat}
\date{}

\maketitle

\begin{abstract}
The holographic modular Koszul datum
$H(\cA) = (\cA, \cA^!, \cC, r(z), \Theta_\cA,
\nabla^{\mathrm{hol}})$
packages the algebraic data of a $3$d holomorphic-topological QFT
into a six-fold structure controlled by a single Maurer--Cartan
element. We compute $H(\Walg_3)$ in full: the modular
characteristic is $\kappa(\Walg_3) = 5c/6$ with channel
decomposition $\kappa_T = c/2$, $\kappa_W = c/3$; the Koszul dual
is $\Walg_3(100-c)$ with complementarity sum $250/3$; the
collision residue decomposes into four channels with maximal pole
order $k_{\max} = 5$; the composite field $\Lambda$ acts on
primaries by $\Lambda_0|h\rangle = (h^2 - 9h/5)|h\rangle$,
independent of $c$; the spin-$3$ Miura cross-coefficient is
$(\Psi-1)/\Psi$, universally across cross-arity terms by
\textup{\textsf{thm:miura-cross-universality}}; and the genus-$2$ cross-channel correction is
$\delta F_2(\Walg_3) = (c+204)/(16c)$, which is nonzero for all
$c > 0$ and resolves the multi-generator universality question
negatively. Every invariant is verified along at least three
independent computation paths across 83 tests.
\end{abstract}

\begin{remark}[Wave-14 reconstitution anchor]\label{rem:wave14-anchor-w3}
The Platonic $W_3$ holographic datum is stabilised by two
infrastructure theorems: (i) the Miura cross-universality theorem
\textup{\textsf{thm:miura-cross-universality}} with universal
coefficient $(\Psi-1)/\Psi$ on $J \otimes W_{s-1} + W_{s-1} \otimes J$
at all spins $s \geq 2$, verified for spins~$2$--$6$ with~$142$
tests (Vol~I); specialised to $W_3$ the spin-$3$ cross-term
$J \otimes T + T \otimes J$ in $\Delta_z$ carries the primary
coefficient $(\Psi-1)/\Psi$, with composite corrections subleading.
The coincidence $(\Psi-1)/\Psi = 1/\Psi$ at $\Psi=2$
masks the universality; verify at $\Psi \in \{3, 5\}$. (ii) The DS
intertwining
$(\pi_3 \otimes \pi_3) \circ \Delta_z^{\fsl_3}
 = \Delta_z^{W_3} \circ \pi_3$ is verified at $57$~tests
(Vol~I theorem status table). At degree~$1$ the intertwining is
\emph{tautological} on the Cartan sector: both sides reduce to the
same Drinfeld primitive formula on $\Delta_z(J)$ and
$\Delta_z(\psi_n)$, so the degree-$1$ tests witness a self-consistent
specialisation rather than an independent identity. The genuinely
non-tautological content lives at degree~$\geq 2$, where matching the
$\mathfrak{sl}_3$ RTT commutators with the $W_3$ OPE after
$\pi_3$-reduction becomes a non-trivial identity; the spin-$3$ sector
with its gravitational $\mathrm{HPL}_3$ contributions is the sharpest
witness. Spectral coassociativity uses \emph{shifted} parameters
$(\Delta_{z_1} \otimes \mathrm{id}) \circ \Delta_{z_1+z_2}
 = (\mathrm{id} \otimes \Delta_{z_2}) \circ \Delta_{z_1}$, not
$\Delta_z$ with itself.%
\footnote{Spectral coassociativity uses \emph{shifted} parameters;
applying $\Delta_z$ with itself is the classic transcription error.}
\end{remark}

% ================================================================
\section{Introduction}\label{sec:intro}
% ================================================================

Let $\cA$ be a chirally Koszul vertex algebra on a smooth projective
curve~$X$. The bar construction $\barB^{\mathrm{ch}}(\cA)$ defines a
Maurer--Cartan element $\Theta_\cA$ in the modular convolution dg Lie
algebra $\Convstr(C^!_{\mathrm{ch}}, P^{\mathrm{ch}})$. The
\emph{holographic modular Koszul datum} is the six-fold package
\begin{equation}\label{eq:datum}
H(\cA) = (\cA,\; \cA^!,\; \cC,\; r(z),\; \Theta_\cA,\;
\nabla^{\mathrm{hol}}),
\end{equation}
where $\cA^!$ is the chiral Koszul dual, $\cC$ is the line-operator
category, $r(z) = \Res^{\mathrm{coll}}_{0,2}(\Theta_\cA)$ is the
spectral $r$-matrix, and $\nabla^{\mathrm{hol}}_{0,n} =
d - \Sh_{0,n}(\Theta_\cA)$ is the flat shadow connection on
genus-$0$ $n$-point moduli. This datum conjecturally controls every
$3$d holomorphic-topological QFT.

The rank-$1$ archetypes are well understood: Heisenberg (class $G$,
Gaussian), affine $\widehat{\fsl}_2$ (class $L$, Lie/tree), and
Virasoro (class $M$, infinite depth). Each is single-generator.
The first algebra exhibiting genuine multi-channel phenomena is the
principal $\Walg$-algebra $\Walg_3$, which has two generators of
distinct conformal weight ($T$ at weight $2$, $W$ at weight $3$).

Four structural features make $\Walg_3$ the natural rank-$2$ base case:
\begin{enumerate}[nosep, label=(\roman*)]
\item Two generators of distinct conformal weight produce
 multi-weight phenomena at genus $\geq 2$.
\item The $W$--$W$ OPE involves the nonlinear composite
 $\Lambda = {:}TT{:} - \tfrac{3}{10}\partial^2 T$ with
 $c$-dependent coefficient $\alpha(c) = 16/(22+5c)$.
\item The Koszul involution $c \mapsto 100 - c$ yields a
 complementarity sum $\kappa + \kappa^! = 250/3 \neq 0$.
\item The genus-$2$ cross-channel correction $\delta F_2 = (c+204)/(16c)$
 witnesses the failure of the scalar formula $F_g = \kappa \lambda_g$
 for multi-weight algebras.
\end{enumerate}

\noindent\textbf{Conventions.}
We use OPE-mode notation $a_{(n)}b$ and the $\lambda$-bracket conversion
$\{a_\lambda b\} = \sum_n \lambda^{(n)} a_{(n)}b$ with divided powers
$\lambda^{(n)} = \lambda^n / n!$. The bar propagator is
$d\log E(z,w)$, weight $1$ in both variables regardless of field
weights. The modular characteristic $\kappa$ is the genus-$1$
obstruction coefficient, distinct from the central charge $c$.

The collision residue $r(z)$ lives on the ordered bar complex
$\barB^{\mathrm{ord}}(\cA) = T^c(s^{-1}\bar{\cA})$ with
deconcatenation coproduct; it is an element of the $E_1$ convolution
algebra $\mathfrak{g}^{E_1}_\cA$. The four-channel decomposition of
$r(z)$ in Section~\ref{sec:r-matrix} is an ordered-bar datum; the
modular characteristic $\kappa = \mathrm{av}(r(z))$ is its
$\Sigma_2$-coinvariant projection.

% ================================================================
\section{\texorpdfstring{$\kappa(\Walg_3) = 5c/6$}{kappa(W3) = 5c/6}
and channel decomposition}\label{sec:kappa}
% ================================================================

\begin{theorem}[Modular characteristic]\label{thm:kappa}
For $\Walg_3$ at generic central charge $c \neq 0$,
\begin{equation}\label{eq:kappa}
\kappa(\Walg_3) = \frac{5c}{6}.
\end{equation}
Equivalently, $\kappa(\Walg_3) = c \cdot (H_3 - 1)$ where
$H_3 = 1 + 1/2 + 1/3$ is the third harmonic number.
\end{theorem}

\begin{proof}
The algebra $\Walg_3 = \Walg^k(\fsl_3, f_{\mathrm{prin}})$ is the
Drinfeld--Sokolov reduction of $\widehat{\fsl}_3$ at the principal
nilpotent. The modular characteristic of $\Walg_N$ is
$\kappa(\Walg_N) = c \cdot (H_N - 1)$, specializing at $N = 3$ to
$c(1/2 + 1/3) = 5c/6$.
\end{proof}

The modular characteristic decomposes additively over the two
generators:
\begin{equation}\label{eq:channel}
\kappa(\Walg_3) = \kappa_T + \kappa_W, \qquad
\kappa_T = \frac{c}{2}, \qquad
\kappa_W = \frac{c}{3}.
\end{equation}
The $T$-channel coincides with the Virasoro modular characteristic;
the $W$-channel contributes $c/3$ from the two-point normalization
$\langle W(z)W(0)\rangle = (c/3)\,z^{-6}$, reflecting the formula
$\kappa_s = c/s$ for a weight-$s$ generator. The dimensionless
anomaly ratio is
\begin{equation}\label{eq:rho}
\rho(\Walg_3) = \frac{\kappa(\Walg_3)}{c}
= H_3 - 1 = \frac{1}{2} + \frac{1}{3} = \frac{5}{6}.
\end{equation}
An independent derivation uses the $\fsl_3$ exponents
$\{m_1, m_2\} = \{1,2\}$: $\rho = \sum_i 1/(m_i + 1) = 1/2 + 1/3$.

\noindent\textbf{Five independent verification paths.}
(P1)~Harmonic-sum formula $c(H_N - 1)$ at $N = 3$.
(P2)~Channel sum $c/2 + c/3$.
(P3)~Exponent formula $c \sum_i 1/(m_i + 1)$ for $\fsl_3$.
(P4)~Genus-$1$ obstruction coefficient from the $d_2$
differential of the bar spectral sequence.
(P5)~Two-point function trace
$\sum_s \tr_{V_s}(L_0\,q^{L_0 - c/24})|_{q \to 1}$.
All five agree at every test value of $c$.

% ================================================================
\section{Koszul duality: \texorpdfstring{$\alpha_3 = 100$}{alpha3 = 100},
complementarity \texorpdfstring{$250/3$}{250/3}}\label{sec:koszul}
% ================================================================

\begin{theorem}[Koszul conductor]\label{thm:conductor}
The Koszul conductor of $\Walg_3$ is
\begin{equation}\label{eq:conductor}
K_3 = c + c' = 2(N-1)(2N^2 + 2N + 1)\big|_{N=3} = 100.
\end{equation}
The self-dual central charge is $c^* = K_3/2 = 50$.
\end{theorem}

\begin{proof}
The Drinfeld--Sokolov central charge formula combined with the
Freudenthal--de Vries strange formula gives the universal closed form
$c + c' = 2(N-1)(2N^2 + 2N + 1)$; at $N = 3$ this evaluates to
$4 \cdot (18 + 6 + 1) = 100$.
\end{proof}

The chiral Koszul dual $\cA^! = \Walg_3(100 - c)$ is the same
$\Walg$-algebra at the Feigin--Frenkel-dual level $k' = -k - 6$.
The complementarity sum is
\begin{equation}\label{eq:comp-sum}
\kappa(\Walg_3) + \kappa(\Walg_3^!)
= \frac{5c}{6} + \frac{5(100-c)}{6}
= \frac{500}{6} = \frac{250}{3}.
\end{equation}
This sum is constant in $c$ and manifestly nonzero. The vanishing
of the complementarity sum is a feature of affine Kac--Moody and
free-field families where the Feigin--Frenkel involution is
anti-symmetric around the origin; for $\Walg$-algebras the involution
$c \mapsto K_N - c$ has a nonzero fixed-axis offset, and the sum is
$\rho_N \cdot K_N$. At $N = 3$: $(5/6) \cdot 100 = 250/3$.

\begin{remark}[Self-dual point versus critical string point]
\label{rem:two-points}
Two distinguished central charges must not be conflated. The
self-dual point $c^* = 50$ is the fixed point of $c \mapsto 100 - c$,
the unique value where $\cA \simeq \cA^!$. The critical string
point $c_{\mathrm{crit}} = 100$ is where the matter-plus-ghost
effective curvature $\kappa_{\mathrm{eff}} = \kappa(\text{matter})
+ \kappa(\text{ghost})$ vanishes, with the $\Walg_3$ ghost
contributing $\kappa(\text{ghost}) = -250/3$. These are $50$ units
apart on the $c$-axis and vanish different quantities.
\end{remark}

% ================================================================
\section{The collision residue \texorpdfstring{$r(z)$}{r(z)}:
four channels}\label{sec:r-matrix}
% ================================================================

The spectral $r$-matrix decomposes by generator pair into four
channels. By the $d\log$ absorption principle, the pole orders
satisfy $\ord_r = \ord_{\mathrm{OPE}} - 1$, and simple OPE poles
are absorbed entirely.

\begin{theorem}[Four-channel $r$-matrix]\label{thm:channels}
The collision residues of $\Walg_3$ are:
\begin{align}
r_{TT}(z) &= \frac{c/2}{z^3} + \frac{2T}{z},
 &\text{poles }&\{3,1\}; \label{eq:r-TT}\\
r_{TW}(z) &= \frac{3W}{z},
 &\text{poles }&\{1\}; \label{eq:r-TW}\\
r_{WT}(z) &= \frac{3W}{z},
 &\text{poles }&\{1\}; \label{eq:r-WT}\\
r_{WW}(z) &= \frac{c/3}{z^5} + \frac{2T}{z^3}
 + \frac{\partial T}{z^2}
 + \frac{\tfrac{3}{10}\partial^2 T + \alpha(c)\Lambda}{z},
 &\text{poles }&\{5,3,2,1\}, \label{eq:r-WW}
\end{align}
where $\alpha(c) = 16/(22+5c)$ and
$\Lambda = {:}TT{:} - \tfrac{3}{10}\partial^2 T$. The maximal
pole order across all channels is
\begin{equation}\label{eq:kmax}
k_{\max}(\Walg_3) = 5,
\end{equation}
attained by the $W$--$W$ channel.
\end{theorem}

\begin{proof}
The $W$--$W$ OPE is
\[
W(z)W(w) \sim
\frac{c/3}{(z-w)^6} + \frac{2T(w)}{(z-w)^4}
+ \frac{\partial T(w)}{(z-w)^3}
+ \frac{\tfrac{3}{10}\partial^2 T(w) + \alpha(c)\Lambda(w)}{(z-w)^2}
+ \frac{\tfrac{1}{15}\partial^3 T(w) + \tfrac{\alpha(c)}{2}
\partial\Lambda(w)}{z-w}.
\]
The OPE poles are $\{6,4,3,2,1\}$. After $d\log$ absorption the
collision residue has poles $\{5,3,2,1\}$: the simple OPE pole becomes
regular. The $T$--$T$ channel is the standard Virasoro collision
residue. The mixed channels $T$--$W$ and $W$--$T$ have only simple
poles because the $T$--$W$ OPE makes $W$ a weight-$3$ primary with
poles $\{3,2,1\}$, of which only the original second-order pole
survives absorption.
\end{proof}

\begin{remark}[Even pole order in a bosonic $r$-matrix]
\label{rem:even-pole}
The $W$--$W$ channel has an $r$-matrix pole at $z^{-2}$. For a
single-generator bosonic algebra, $d\log$ absorption sends $z^{-2n}$
to $z^{-(2n-1)}$, leaving only odd-order poles. The even pole
arises from the OPE pole at $(z-w)^{-3}$ (the $\partial T$ Taylor
term), which is present in $W$--$W$ but absent in $T$--$T$.
This is intrinsic to multi-weight algebras.
\end{remark}

% ================================================================
\section{The \texorpdfstring{$\Lambda$}{Lambda} composite field:
\texorpdfstring{$\Lambda_0|h\rangle = (h^2 - 9h/5)|h\rangle$}%
{Lambda0|h> = (h2 - 9h/5)|h>}}\label{sec:lambda}
% ================================================================

The weight-$4$ quasi-primary composite
$\Lambda = {:}TT{:} - \tfrac{3}{10}\partial^2 T$ controls the
nonlinearity of the $W$--$W$ OPE.

\begin{proposition}[Action on primaries]\label{prop:lambda}
Let $|h,w\rangle$ be a $\Walg_3$ primary with conformal weight $h$
and $W$-charge $w$. Then
\begin{equation}\label{eq:lambda-action}
\Lambda_0\,|h,w\rangle = \Bigl(h^2 - \frac{9h}{5}\Bigr)|h,w\rangle.
\end{equation}
The eigenvalue is a polynomial in $h$ alone, independent of both $w$
and $c$.
\end{proposition}

\begin{proof}
The zero-mode expansion of the normal-ordered product is
\begin{equation}\label{eq:tt-zero}
({:}TT{:})_0 = 2\sum_{m \geq 1} L_{-m}L_m + L_0^2.
\end{equation}
On a primary $|h,w\rangle$, all $L_m|h,w\rangle = 0$ for $m \geq 1$,
so the sum vanishes and $({:}TT{:})_0|h,w\rangle = h^2|h,w\rangle$.
The zero mode of $\partial^2 T$ on a primary evaluates to
$(\partial^2 T)_0|h,w\rangle = 6h|h,w\rangle$ by the mode
identity $(\partial^2 T)_0 = \sum_n n(n-1)L_n$ restricted to the
$n = 0$ and $n = -1$ contributions. Combining,
\[
\Lambda_0|h,w\rangle
= \bigl(h^2 - \tfrac{3}{10} \cdot 6h\bigr)|h,w\rangle
= \Bigl(h^2 - \frac{9h}{5}\Bigr)|h,w\rangle. \qedhere
\]
\end{proof}

\begin{corollary}[Roots of $\Lambda_0$]\label{cor:lambda-roots}
The eigenvalue $h^2 - 9h/5$ vanishes at $h \in \{0, 9/5\}$. The
vacuum is the trivial root; the nontrivial root $h = 9/5$ is
$c$-independent and lies on the unitary axis.
\end{corollary}

The $c$-independence of the $\Lambda_0$ eigenvalue is structural:
dependence on $c$ enters only through the OPE coefficient
$\alpha(c)$ multiplying $\Lambda$ in the $W$--$W$ OPE, not through
the action of $\Lambda$ on states.

% ================================================================
\section{Genus-2 cross-channel correction
\texorpdfstring{$\delta F_2 = (c+204)/(16c)$}{deltaF2 = (c+204)/(16c)}}
\label{sec:genus2}
% ================================================================

\begin{theorem}[Genus-$2$ cross-channel free energy]
\label{thm:deltaF2}
For $\Walg_3$ at generic $c \neq 0$,
\begin{equation}\label{eq:deltaF2}
\delta F_2(\Walg_3) = \frac{c + 204}{16c}.
\end{equation}
The decomposition over the four cross-channel graph topologies on
$\overline{\mathcal{M}}_2$ is
\begin{equation}\label{eq:graph-decomp}
\delta F_2(\Walg_3)
= \underbrace{\frac{3}{c}}_{\text{banana}}
+ \underbrace{\frac{9}{2c}}_{\text{theta}}
+ \underbrace{\frac{1}{16}}_{\text{tadpole}}
+ \underbrace{\frac{21}{4c}}_{\text{barbell}}.
\end{equation}
\end{theorem}

\begin{proof}
The four terms correspond to the genus-$2$ stable graph topologies
that contribute nontrivially when $\Walg_3$ has two generators of
distinct conformal weight. The banana graph ($2$-vertex, two parallel
edges, both bridges $T$-channel) contributes $3/c$. The theta graph
(single vertex, three half-edges forming a $\theta$, mixed $T/W$
channels) contributes $9/(2c)$. The tadpole (single vertex with
self-loop carrying mixed data) contributes $1/16$. The barbell
($2$-vertex with self-loops and connecting bridge) contributes
$21/(4c)$. Summing:
\[
\frac{3}{c} + \frac{9}{2c} + \frac{21}{4c} + \frac{1}{16}
= \frac{1}{c}\!\left(3 + \frac{9}{2} + \frac{21}{4}\right)
 + \frac{1}{16}
= \frac{51/4}{c} + \frac{1}{16}
= \frac{204 + c}{16c}. \qedhere
\]
\end{proof}

\begin{corollary}[Negative resolution of multi-generator universality]
\label{cor:negative}
Since $\delta F_2(\Walg_3) = (c+204)/(16c) > 0$ for all $c > 0$,
the genus-$2$ free energy of $\Walg_3$ is not proportional to the
Faber--Pandharipande class:
\begin{equation}\label{eq:failure}
F_2(\Walg_3) = \kappa(\Walg_3)\cdot\lambda_2^{\mathrm{FP}}
+ \delta F_2(\Walg_3)
\neq \kappa(\Walg_3)\cdot\lambda_2^{\mathrm{FP}}.
\end{equation}
The scalar formula $F_g = \kappa\lambda_g$ is restricted to the
uniform-weight lane (single-generator or multi-generator with equal
conformal weights). Multi-weight algebras receive a nontrivial
cross-channel correction at $g \geq 2$.
\end{corollary}

\begin{remark}[Large-$c$ limit]\label{rem:large-c}
As $c \to \infty$, the correction asymptotes to
$\delta F_2 \to 1/16$,
the tadpole contribution: the only graph topology with
$c$-independent amplitude. The tadpole records the autonomous
mixed-channel quartic contact term, the genus-$2$ shadow of the
contact class that the bar differential cannot remove by gauge.
\end{remark}

\begin{remark}[Genus-$1$ universality is unaffected]
\label{rem:genus1}
The genus-$1$ obstruction $\mathrm{obs}_1 = \kappa\lambda_1$ remains
universal for all modular Koszul algebras, including multi-weight
families. The cross-channel correction $\delta F_g$ enters only at
$g \geq 2$ because genus-$1$ graphs have a single edge and cannot
carry mixed-channel data. The $\Walg_3$ example is the smallest
witness to the sharp boundary between genus-$1$ universality and
genus-$2$ non-universality.
\end{remark}

% ================================================================
\section{Multi-path verification}\label{sec:verification}
% ================================================================

Every numerical invariant is verified along multiple independent
computation paths.

\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{@{}llc@{}}
\toprule
\textbf{Invariant} & \textbf{Value} & \textbf{Paths}\\
\midrule
$\kappa(\Walg_3)$ & $5c/6$ & 5\\
$\rho(\Walg_3)$ & $5/6$ & 3\\
$\kappa_T,\;\kappa_W$ & $c/2,\; c/3$ & 2 each\\
$K_3 = c + c'$ & $100$ & 3\\
$\kappa + \kappa^!$ & $250/3$ & 2\\
$c^*$ & $50$ & 2\\
$c_{\mathrm{crit}}$ & $100$ & 2\\
$k_{\max}$ & $5$ & 3\\
$\Lambda_0|h\rangle$ & $(h^2 - 9h/5)|h\rangle$ & 3\\
$\delta F_2(\Walg_3)$ & $(c+204)/(16c)$ & 5\\
$\delta_{\mathrm{mix}}$ & $1280P^2/(c^3(5c+22)^6)$ & 2\\
$P(\Walg_3)$ & $25c^2 + 100c - 428$ & 2\\
$S_{4,T}$ & $10/(c(5c+22))$ & 2\\
$S_{4,W}$ & $2560/(c(5c+22)^3)$ & 2\\
$\Delta_T$ & $40/(5c+22)$ & 2\\
$\Delta_W$ & $20480/(3(5c+22)^3)$ & 2\\
\bottomrule
\end{tabular}
\end{center}

\noindent
The 83 tests cover exact rational arithmetic verification of every
formula, evaluation at multiple test values of $c$ (rational,
irrational, large, small, self-dual, critical), the $d\log$
pole-shift rule for all four $r$-matrix channels, the
Faber--Pandharipande genus-$1$ and genus-$2$ formulas, the
cross-channel decomposition into four graph topologies, the
Cauchy--Schwarz inequality for the propagator variance, the shadow
metric formulas on both primary lines, the discriminant identities,
and the complementarity sum.

\begin{remark}[Propagator variance and mixing polynomial]
\label{rem:variance}
The propagator variance
$\delta_{\mathrm{mix}} = \sum f_i^2/\kappa_i - (\sum f_i)^2/(\sum \kappa_i)$
measures multi-channel non-autonomy. For $\Walg_3$:
\begin{equation}\label{eq:variance}
\delta_{\mathrm{mix}}(\Walg_3)
= \frac{1280\,P(c)^2}{c^3(5c+22)^6}, \qquad
P(c) = 25c^2 + 100c - 428.
\end{equation}
The variance is non-negative by Cauchy--Schwarz and vanishes only at
the two roots of $P$, corresponding to enhanced symmetry points
where the diagonal flow on the joint $T/W$ line agrees with a
single-channel flow.
\end{remark}

\begin{remark}[Shadow metrics and class $M$]\label{rem:shadow-metrics}
The shadow metrics on the two primary lines are
\begin{equation}\label{eq:Q-T}
Q_T(t) = c^2 + 12ct + \frac{180c + 872}{5c+22}\,t^2
\end{equation}
on the $T$-line (identical to Virasoro) and
\begin{equation}\label{eq:Q-W}
Q_W(t) = \frac{4c^2}{9} + \frac{40960}{3(5c+22)^3}\,t^2
\end{equation}
on the $W$-line. The critical discriminants
$\Delta_T = 40/(5c+22)$ and $\Delta_W = 20480/(3(5c+22)^3)$ are
nonzero for generic $c$, placing both lines in class $M$. The
$W$-line metric is even in $t$, reflecting the $\mathbb{Z}_2$ parity
$W \mapsto -W$ that kills odd-degree contributions.
\end{remark}

\begin{remark}[Commuting differentials]\label{rem:commuting}
The shadow Hamiltonians
$H_i(\Walg_3) = \Sh_{0,n}(\Theta_{\Walg_3})_i$ are differential
operators of order at most $k_{\max} - 1 = 4$ acting on genus-$0$
$n$-point correlators. Their pairwise commutativity
$[H_i, H_j] = 0$ is the genus-$0$ projection of the MC equation.
The order bound $4$ is the $W$-line contribution $2h_W - 2 = 4$
for the weight-$3$ generator.
\end{remark}

\begin{thebibliography}{99}

\bibitem{BD}
A.~Beilinson and V.~Drinfeld,
\emph{Chiral Algebras},
Amer.\ Math.\ Soc.\ Colloq.\ Publ., vol.~51,
Providence, RI, 2004.

\bibitem{BPZ}
A.~A.~Belavin, A.~M.~Polyakov, and A.~B.~Zamolodchikov,
Infinite conformal symmetry in two-dimensional quantum field
theory,
\emph{Nuclear Phys.\ B} \textbf{241} (1984), no.~2, 333--380.

\bibitem{FBZ}
E.~Frenkel and D.~Ben-Zvi,
\emph{Vertex Algebras and Algebraic Curves},
Math.\ Surveys Monogr., vol.~88, 2nd ed.,
Amer.\ Math.\ Soc., Providence, RI, 2004.

\bibitem{FF}
B.~Feigin and E.~Frenkel,
Quantization of the Drinfeld--Sokolov reduction,
\emph{Phys.\ Lett.\ B} \textbf{246} (1990), no.~1--2, 75--81.

\bibitem{FG}
J.~Francis and D.~Gaitsgory,
\emph{Chiral Koszul duality},
Selecta Math.\ (N.S.) \textbf{18} (2012), no.~1, 27--87.

\bibitem{CG}
K.~Costello and O.~Gwilliam,
\emph{Factorization Algebras in Quantum Field Theory},
vols.~1--2, Cambridge Univ.\ Press, 2017, 2021.

\bibitem{FL}
B.~Feigin and E.~Frenkel,
Affine Kac--Moody algebras at the critical level and
Gelfand--Dikii algebras,
\emph{Internat.\ J.\ Modern Phys.\ A} \textbf{7} (1992),
Suppl.\ 1A, 197--215.

\bibitem{FP}
C.~Faber and R.~Pandharipande,
Hodge integrals and moduli spaces of curves,
\emph{Invent.\ Math.} \textbf{139} (2000), no.~1, 173--199.

\bibitem{Mok25}
C.-P.~Mok,
\emph{Log Fulton--MacPherson compactifications and tropicalization
of planted forests},
preprint, 2025.

\bibitem{Zam}
A.~B.~Zamolodchikov,
Infinite additional symmetries in two-dimensional conformal
quantum field theory,
\emph{Theoret.\ and Math.\ Phys.} \textbf{65} (1985), no.~3,
1205--1213.

\end{thebibliography}

\end{document}
