% ======================================================================
% GUIDE TO MAIN RESULTS
% A compact reference for the five main theorems and their dependencies.
% ======================================================================

\chapter*{Guide to main results}
\addcontentsline{toc}{chapter}{Guide to main results}
\label{ch:guide}%

\noindent
The principal results below are stated with their labels, locations,
ambient categories, and hypotheses. The five theorem surfaces are
separated into unconditional adjunction data, Koszul-locus
quasi-isomorphisms, completed coderived statements, and conditional
geometric refinements for augmented chiral algebras~$\cA$ on a smooth
projective curve~$X$ satisfying the standing finiteness conditions
(\S\ref{sec:standing-assumptions}).

\medskip

\subsection*{The ordered bar and averaging}
\label{subsec:guide-ordered-bar-record}

The local seed of the volume is the logarithmic collision form
$\eta_{ij}=d\log(z_i-z_j)$ on ordered configuration spaces. Arnold's
three-term relation supplies the configuration-space part of
nilpotence for the ordered bar coalgebra
\[
 \barB^{\mathrm{ord}}_X(\cA)=T^c(s^{-1}\bar\cA),
 \qquad |s^{-1}v|=|v|-1,
\]
while the chiral multiplication, internal differential, and curvature
terms supply the algebraic part of the bar differential. In the ordered
model the universal Maurer--Cartan element is
\[
 \Theta_\cA^{\mathrm{ord}}\in \MC(\mathfrak g_{\cA}^{\Eone}),
 \qquad
 D\Theta_\cA^{\mathrm{ord}}
 +\tfrac12[\Theta_\cA^{\mathrm{ord}},\Theta_\cA^{\mathrm{ord}}]=0.
\]
Its degree-two local component is the collision residue
$r_\cA(z)$; its scalar projection is the modular characteristic
$\kappa(\cA)$. On the uniform-weight scalar-diagonal lane,
Theorem~D gives the fibre-curvature identity
\[
 (d^{\mathrm{ord}}_{\mathrm{fib}})^2
 =\kappa(\cA)\cdot\omega_g,
 \qquad
 \omega_g=c_g(\mathbb{E}),
\]
against the Hodge bundle $\mathbb{E}=\pi_*\omega_\pi$ on the universal
curve. For multi-weight algebras at $g\ge2$ the scalar term is only the
diagonal contribution; the cross-channel correction is the separate
term of Theorem~\ref{thm:multi-weight-genus-expansion}.

The symmetric modular class is the derived quotient of the ordered datum under
averaging:
\[
 \mathrm{av}\colon
 \mathfrak g^{\Eone}\longrightarrow \mathfrak g^{\mathrm{mod}},
 \qquad
 \mathrm{av}_n=\frac1{n!}\sum_{\sigma\in S_n}\sigma^*.
\]
For $\Einf$-chiral input the symmetric and ordered models agree on the
formal commutative surface. For genuinely $\Eone$-chiral input the
$\mathrm{GRT}_1(\mathbb Q)$-dependent ordered kernel is erased by
$\mathrm{av}$; averaging is not an equivalence. The Vol~I
standard-landscape quadrichotomy is
$\mathsf G/\mathsf L/\mathsf C/\mathsf M$ with shadow depths
$2/3/4/\infty$. Extended comparison rows used later adjoin
\[
\mathsf M^{\mathrm{ext}}\quad\text{and}\quad\mathsf B,
\]
where $\mathsf B$ is the Vol~III Mukai/K3 witness rather than a fifth
Vol~I archetype. The witnesses are Heisenberg, affine Kac--Moody at
non-critical level, $\beta\gamma$, Virasoro with principal
$\mathcal W_N$ extensions, subregular or hook Drinfeld--Sokolov
reductions such as Bershadsky--Polyakov, and the K3
Borcherds--Kac--Moody object $\mathbf H_{\Delta_5}$. The critical
affine stratum is a boundary where Sugawara degenerates, not another
row.

\medskip
\noindent\textbf{Five derived evaluations.}\enspace
Theorem~A has two distinct assertions. First, the chiral bar--cobar
adjunction
\[
\Omega_X^{\mathrm{ch}}\dashv \barB_X^{\mathrm{ch}}
\]
exists for augmented chiral algebras in the stated holonomic
factorization ambient; this produces the unit and counit, not a
quasi-isomorphism. Second, on a chiral Koszul pair the unit and counit
are equivalences in the complete conilpotent factorization categories,
and Verdier duality identifies
$\mathbb D_{\operatorname{Ran}}\barB_X^{\mathrm{ch}}(\cA)$ with the
homotopy Koszul-dual factorization algebra $\cA^!_\infty$. The formula
$\Omega_X\barB_X(\cA)\simeq\cA$ is inversion; the formula
$\mathbb D_{\operatorname{Ran}}\barB_X(\cA)\simeq\cA^!_\infty$ is the
Koszul-dual route.

Theorem~B is the inversion surface. On the strict Koszul locus the
counit $\Omega_X(\barB_X(\cA))\to\cA$ is a quasi-isomorphism. Off that
strict lane the comparison is made in completed coderived or
contraderived ambients under the stated Mittag--Leffler hypotheses; no
raw direct-sum class-$\mathsf M$ quasi-isomorphism is asserted. For
$\mathbf H_{\Delta_5}$ over $\overline{\mathcal A}_2$, the strict
locus is the admissible-Humbert complement
\[
 U^{\mathrm{adm}}
 =\overline{\mathcal A}_2
 \setminus\bigcup_{n\ \mathrm{admissible}}H_n,
\]
where admissibility is the Bruinier singular-theta obstruction
condition of Remark~\ref{rem:tbsp-why-admissibility}. Off the strict
lane the weight-completed chiral bar coalgebra carries the
coderived/contraderived Positselski equivalence. The chain-level
octachotomy has the eight strata recorded in
Corollary~\ref{thm:codim4-admissible-heegner-emptiness}: Koszul locus,
codimension-one single-monodromy, codimension-two bi-unipotent
Deligne--Malcev, admissible-Heegner Malcev ladder, codimension-three
tri-unipotent extension, Baily--Borel zero-cusp, weight-completed
coderived, and the $A_\infty$-corrected neighbourhood of $H_3$.
The Eichler--Zagier congruence $n\equiv3,5\bmod8$ belongs to the
separate pentagon/Humbert obstruction filter. The first non-empty
admissible Heegner triple is $H_3\cap H_4\cap H_7$, realised by
$[E_{\sqrt{-3}}\times E_{\sqrt{-7}}]$ on $\overline{\mathcal A}_2$;
the corresponding quadruple intersections are empty.

Theorem~C is derived-centre complementarity. C0 identifies the chiral
derived centre with
\[
 \mathcal Z^{\mathrm{der}}_{\mathrm{ch}}(\cA)
 =\operatorname{RHom}_{\cA\otimes\cA^{\mathrm{op}}}(\cA,\cA).
\]
The identification is unconditional in the coderived category and
ordinary-derived on the flat perfect locus. C1 gives the Verdier
eigenspace decomposition for all genera, with duality and Lagrangian
polarization for $g\ge1$ and genus~$0$ treated separately. C2 is the
shifted-symplectic/BV realization on the BV-perfect,
Verdier-nondegenerate, uniform-weight-perfect bar-chart surface. On the
canonical landmark witnesses
\[
 \kappa(\cA)+\kappa(\cA^!)
 \in\{0,8,13,250/3,98/3\},
\]
with $8$ the Vol~III $\mathsf B$-row Mukai witness; this is a landmark
bucket, not a universal bound.

Theorem~D is the all-weight genus expansion
\[
 F_g(\cA)=\kappa(\cA)\lambda_g^{\mathrm{FP}}
 +\delta F_g^{\mathrm{cross}}(\cA).
\]
On the uniform-weight scalar-diagonal lane the correction vanishes and
$\mathrm{obs}_g(\cA)=\kappa(\cA)\lambda_g$ with
$\lambda_g=c_g(\mathbb{E})$. Universally
$\delta F_1^{\mathrm{cross}}=0$. For $\mathcal W_3$ at genus~$2$ the
cross-channel correction is
\[
 \delta F_2^{\mathrm{cross}}(\mathcal W_3)=\frac{c+204}{16c}.
\]

Theorem~H is the curve-level chiral Hochschild theorem, not a
topological or categorical Hochschild statement. On the proved
Koszul/generic surface with $E_\infty$-chiral PBW completion,
\[
 P(t,q)=\mathrm{HS}_{Z(\cA)}(q)
 +\mathrm{HS}_{\ChirHoch^1(\cA)}(q)t
 +\mathrm{HS}_{Z(\cA^!)}(q)t^2.
\]
The Calabi--Yau higher-degree shadows, including the degree-three
K3$\times E$ class
\[
 \chi_3={:}T\partial T{:}-\tfrac14\partial^3T
 +\hbar\,\mathrm{qt}(J^{(3)}),
\]
belong to the Vol~III companion lane, where the pairing with the
K3$\times E$ generator gives
\[
 \langle[\chi_3],[e_3^{\,\mathrm{K3}\times E}]\rangle
 =2\,\mathrm{Vol}(E)(2\pi i)^3
 =\chi(\mathcal O_{\mathrm{K3}})
 \Res_{s=1/2}[E_5^{(2)}(Z,s)]\big|_{K(1)}.
\]
Those classes refine the cross-volume picture; they are not the
curve-level statement of Theorem~H.

Positselski inversion is the closure step. Once Theorem~B recovers the
object in the correct ambient, Theorems~C, D, and H act on the
recovered chiral coalgebra. Without B the derived centre has no
canonical object, the Hodge-weighted fibre has no anchor, and bounded
$\mathcal D_C$-support has no ambient.

\medskip
\noindent\textbf{The collision residue.}\enspace
The classical residue $r_\cA(z)$ has seven faces organised in three
tiers. Tier~I records intrinsic OPE data and the
shifted-symplectic/BV datum on its perfect locus:
\[
 r^{\mathrm{Heis}}_k(z)=\frac{k}{z},
 \qquad
 r^{\mathrm{KM},\fg}_k(z)=\frac{k\,\Omega_{\mathrm{tr}}}{z},
 \qquad
 r^{\mathrm{Vir}}_c(z)=\frac{c/2}{z^3}+\frac{2T}{z}.
\]
Tier~II is the $E_d$-holomorphic factorisation-algebra braiding,
pinned up to the $\mathrm{GRT}_1(\mathbb Q)$ torsor by
Willwacher's $H^0(\mathsf{GC}_2)=\mathfrak{grt}_1$. Tier~III is the
Stage-2 chiral quantum-group output: Maulik--Okounkov spectral
$R$-matrix on $\mathrm{Hilb}^{[n]}(\mathrm{K3})$, Drinfeld RTT
current via the associative bar multiplication, and Belavin elliptic
non-dynamical $R$-matrix. Cross-tier maps specialise from Tier~I to
Tier~II to Tier~III; intra-tier maps are
$\mathrm{GRT}_1(\mathbb Q)$-gauge equivalences.

\medskip
\noindent\textbf{Operadic ladder.}\enspace
The derived chiral centre sits on the $E_n$ ladder: $\Eone$-chiral
input gives an $\Etwo$ centre; $\Einf$-chiral input gives an
$\Ethree$ centre through Higher Deligne; the Drinfeld centre supplies
braiding when $\Eone$ lifts to $\Etwo$. Sugawara topologisation at
non-critical level promotes $\Eone$-chiral data to
$E_3^{\mathrm{top}}$ on $Q_{\mathrm{tot}}$-cohomology for affine
Kac--Moody and for principal $\mathcal W_N$ at non-critical level.
Class~$\mathsf M$ is unconditional on the pro-object,
$J$-adic/weight-completed, and coderived ambients. Non-principal
Drinfeld--Sokolov reductions, $\mathcal W_\infty$, the critical
stratum, and logarithmic $\mathcal W(p)$ carry the scope qualifiers
recorded in the concordance. For simple $\mathfrak g$ at non-critical
level, Theorem~\ref{thm:e3-identification} identifies the
$E_3^{\mathrm{top}}$ formal deformation family of the derived chiral
centre of $V_k(\mathfrak g)$ with
\[
 \hbar H^3(\mathfrak g)[[\hbar]],
\]
and matches it with the Costello--Francis--Gwilliam perturbative
Chern--Simons $E_3$-algebra on the formal disk.

\medskip
\noindent\textbf{Three-volume comparison.}\enspace
On the checked surfaces the three volumes form the diagram
\[
\begin{array}{ccc}
\mathrm{CY}_d^{\mathrm{cat}}
& \xrightarrow{\;\Phi^{\mathrm{FA}}_d\;}
& \mathrm{Fact}^{\mathrm{hol}}_{E_d}(X) \\[2pt]
\big\downarrow\,{\scriptstyle\mathrm{Shad}_\bullet}
& & \big\downarrow\,{\scriptstyle
\mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}} \\[2pt]
\mathrm{Alg}_{\Eone^{\mathrm{ch}}}(C)
& \xleftarrow[\;\Omega_C^{\mathrm{ch}}\;]{\barB_C^{\mathrm{ch}}}
& \mathrm{CoAlg}^{\mathrm{fact}}_{\Eone^{\mathrm{ch}}}(C).
\end{array}
\]
Volume~I is the bottom-row operadic reading. Volume~II is the
holographic reading: $\mathsf{SC}^{\mathrm{ch,top}}$ governs the
derived-centre pair $(C^\bullet_{\mathrm{ch}}(\cA,\cA),\cA)$, and
topologisation produces the $3$d holomorphic-topological bulk where
the DVV--DMVV inverse Igusa form $1/\Phi_{10}^{\mathrm{un}}$
appears on its BPS scope.
Volume~III is the geometric reading: the two-stage functor
\[
 \Phi_d=
 \mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}\circ\Phi_d^{\mathrm{FA}}
\]
first produces an $E_d$-holomorphic factorisation algebra and then
specialises by factorisation homology over $\Sigma_{d-1}$ followed by
restriction to a reference curve~$C$. A single Calabi--Yau category
therefore gives a family of chiral shadows indexed by
$(\Sigma_{d-1},C)$.

On the K3 lane the Stage-2 shadow has local positive-half Rees charts
where Hall multiplication and hCS extension gluing agree. The compact
Hall--Drinfeld/Borcherds object is the conditional global comparison
\[
 \mathbf H_{\Delta_5}
 =\mathcal D_\hbar\!\left(
 \mathcal Y^{\mathrm{Hall}}_\hbar(\mathrm{CoHA}_{\mathrm{K3}\times E}),
 \widetilde\Phi_{\mathrm{Sp}_4}^{\mathrm{Sieg\text{-}Bor}}
 [\Phi_{10}^{\mathrm{un}}/\eta^{24}],
 R_{\mathrm{Sieg,dyn}}\right),
 \qquad \hbar^2=-\frac18.
\]
Vol~III constructs the resolved-conifold hCS \(E_3\)-descent, its
anomaly-free perturbative quantum lift, and the finite positive-half
hCS--Rees-Hall chart maps.  The quasi-NCCR and compact Hall-double
identifications are hypotheses for this global display, not
consequences of those local toric constructions.
Four Yangian types
$Y_\hbar(\mathfrak g)$, $Y_\hbar^{\mathrm{dg}}(\mathfrak g)$,
$Y^{\mathrm{ch}}(\mathfrak g)$, and $Y^{\mathrm{spec}}$ separate the
Drinfeld, dg-shifted, chiral, and spectral outputs. Four
$\Psi$-siblings
$\{\Psi,\Psi^{\deg},\Psi^{\mathrm{tor}},\Psi^{\mathrm{metap}}\}$
record the reflective interior, Klingen cusp, Humbert divisor, and
metaplectic branch of the Stage-2 output.
The Borcherds weight identity is
\[
 \kappa_{\mathrm{BKM}}(\Phi_N)=\frac{c_N(0)}2.
\]
The programme Gritsenko family has
$c_N(0)=(10,8,6,4,2)$ and weights $(5,4,3,2,1)$ for
$N\in\{1,2,3,4,6\}$. The singly-twined $M_{23}$ family has
$c_N(0)=(10,4,2,2,2)$ and weights $(5,2,1,1,1)$ on the same index
set. The physical CHL family has weights
$24/(N+1)-2=(10,6,4,2,1,0)$ on
$N\in\{1,2,3,5,7,11\}$. The Cl\'ery--Gritsenko 8-form atlas has weights
$(5,2,1,1,\tfrac12,1,\tfrac14,0)$ at $N\in\{1,\ldots,8\}$, with cover
assignment
$\mathrm{Sp}_4(\mathbb Z)/\mathrm{Mp}_4/\widetilde{\mathrm{Mp}}_4$ by
weight-integrality class. The notation $\Phi_N$ is therefore
unambiguous only after the input Jacobi form is named.

The universal trace identity on its scoped rows is
\[
 \hbar^2K=-1,\qquad K=2c_+(L).
\]
The K3 $\mathsf B$-row has $(K,\hbar^2)=(8,-1/8)$ from the Mukai
lattice $\mathrm{II}_{4,20}$; Monster has $(2,-1/2)$ on
$\mathrm{II}_{1,1}$; Fake Monster has $(50,-1/50)$ on
$\mathrm{II}_{25,1}$; Enriques has the canonical $K=4$ reading on
its signature-$(2,10)$ Mukai lattice. The Conway-metaplectic branch is
a structural boundary of the identity rather than an independent
reflective-crown row: the Monster-transported $(2,-1/2)$ reading
survives, while positive-definite and hyperbolic completions do not
give a four-route conductor witness.
At the K3 row the value $K=8$ has three convergent readings: Mukai
$2c_+(\mathrm{II}_{4,20})=8$, Humbert monodromy around $H_1$, and
Lusztig reflection length $\ell_{\zeta_8}=8$. They agree because the
identity component $\mathrm{Aut}^\circ(\mathrm{K3}\times E)=E$ has no
$\mathbb G_m$ subtorus, so the K-theoretic CoHA has no
$(q_1,q_2)$-deformation separating the three readings.

\medskip

\renewcommand{\arraystretch}{1.3}
\begin{longtable}{@{}p{2.2cm}p{7.7cm}p{3.0cm}@{}}
\textsc{Label} & \textsc{Statement} & \textsc{Location} \\
\hline
\endfirsthead
\textsc{Label} & \textsc{Statement} & \textsc{Location} \\
\hline
\endhead
\textbf{Theorem A} &
 Bar--cobar adjunction in two lanes: chain-level adjunction with the
 universal twisting morphism and Fulton--MacPherson counit witness,
 and factorization-$\infty$ adjunction on $\operatorname{Ran}(X)$;
 Verdier duality identifies
 $\mathbb{D}_{\operatorname{Ran}} \bar{B}_X(\cA)
 \simeq \cA^!_\infty$ (factorization \emph{algebra}, not coalgebra). &
 Thms~\ref{thm:bar-cobar-adjunction},
 \ref{thm:bar-cobar-isomorphism-main},
 \ref{thm:A-infinity-2} \\[4pt]

\textbf{Theorem B} &
 Bar--cobar inversion in ambient-qualified form: strict
 quasi-isomorphism on the Koszul locus; weight-completed coderived
 Positselski equivalence for
 $\widehat{C}=\widehat{\bar{B}}^{\mathrm{ch}}(\cA)$ in holonomic
 factorization $\mathcal{D}$-modules; raw direct-sum class-$M$ failure
 explicit. &
 Thms~\ref{thm:higher-genus-inversion},
 \ref{thm:bar-cobar-inversion-qi},
 \ref{thm:chiral-positselski-weight-completed},
 \ref{thm:tbsp-global-inversion-all-admissible};
 Prop.~\ref{prop:chiral-positselski-raw-direct-sum-class-M-false}
 \\[4pt]

\textbf{Theorem C} &
Complementarity: C0/C1 decomposition and Lagrangian duality on their
proved ambients, with the shifted-symplectic C2 refinement realised on the
BV-perfect, Verdier-nondegenerate, uniform-weight-perfect surface; the
verified scalar Verdier sums form the classical
$\mathsf{G}/\mathsf{L}/\mathsf{C}/\mathsf{M}$ ceiling
$\{0,13,\frac{250}{3},\frac{98}{3}\}$, enlarged to the canonical
bucket $\{0,8,13,\frac{250}{3},\frac{98}{3}\}$ by the Vol~III
$\mathsf{B}$-row Mukai witness at $K^\kappa=8$. &
Thm~\ref{thm:quantum-complementarity-main};
Thm~\ref{thm:derived-centre-complementarity-strengthened};
Convention~\ref{conv:theorem-c-bucket};
Thm~\ref{thm:shifted-symplectic-complementarity} \\[4pt]

\textbf{Theorem D} &
 Modular characteristic:
 $F_g(\cA)=\kappa(\cA)\lambda_g^{\mathrm{FP}}
 + \delta F_g^{\mathrm{cross}}(\cA)$ at all genera; on the
 uniform-weight scalar-diagonal lane $\delta F_g^{\mathrm{cross}}=0$, so
 $\mathrm{obs}_g(\cA)=\kappa(\cA)\lambda_g$ with
 $\lambda_g=c_g(\mathbb{E})$. &
 Thms~\ref{thm:modular-characteristic},
 \ref{thm:multi-weight-genus-expansion} \\[4pt]

\textbf{Theorem H} &
 Chiral Hochschild only: derived duality and concentration in
 degrees $\{0,1,2\}$ on the proved Koszul/generic surface, with
 polynomial growth; critical affine and non-generic class-$M$
 parameters lie outside. The Swiss-cheese structure lives on
 $(C^\bullet_{\mathrm{ch}}(\cA,\cA),\cA)$, not on $\barB(\cA)$. &
 Thms~\ref{thm:main-koszul-hoch},
 \ref{thm:hochschild-polynomial-growth};
 Prop.~\ref{prop:chirhoch1-affine-km} \\[4pt]

\hline\\[-8pt]
\multicolumn{3}{@{}l}{\textsc{Additional principal results}} \\[2pt]
\hline

\textbf{Koszulness} &
 Twelve characterizations of chiral Koszulness:
 eight genuinely independent bidirectional equivalences
 ((i)--(v), (ix)--(x), and the genus-$0$ clause of (vii));
 Barr--Beck--Lurie monadicity (vi) as listed consequence of (v);
 chiral Hochschild concentration and duality (viii) as one-way
 consequence on the Koszul locus; Lagrangian criterion (xi)
 conditional on perfectness/nondegeneracy;
 $\mathcal{D}$-module purity (xii) one-directional
 ((xii)$\Rightarrow$(x) proved; converse proved for affine
 Kac--Moody at non-critical level, open for Virasoro and
 $\mathcal{W}$). &
 Thm~\ref{thm:koszul-equivalences-meta} \\[4pt]

\textbf{MC1 (PBW)} &
 PBW spectral sequence degenerates at $E_2$ for all
 standard families (Kac--Moody, Virasoro, $\cW_N$,
 free fields, lattice). &
 Prop~\ref{prop:pbw-universality} \\[4pt]

\textbf{MC2 ($\Theta_\cA$)} &
 Bar-intrinsic construction of the universal MC element:
 $\Theta_\cA := D_\cA - \dzero$ is MC because $D_\cA^2 = 0$.
 Scalar saturation proved for all algebraic families. &
 Thm~\ref{thm:mc2-bar-intrinsic} \\[4pt]

\textbf{MC3 (all types)} &
 All-types categorical prefundamental Clebsch--Gordan closure
 with the DK comparison on the evaluation-generated core; the
 extension beyond the evaluation-generated core remains open. &
 Cor~\ref{cor:mc3-all-types} \\[4pt]

\textbf{MC4} &
 Strong completion-tower theorem:
 completed bar--cobar homotopy equivalence on
 $\CompCl(\mathcal{F}_{\mathrm{ft}})$. &
 Thm~\ref{thm:completed-bar-cobar-strong} \\[4pt]

\textbf{MC5 (genus tower)} &
 (1)~Analytic HS-sewing \textbf{proved}: polynomial OPE growth $+$
 subexponential sector growth $\Longrightarrow$ convergence at
 all genera; Heisenberg sewing via Fredholm determinant.
 (2)~Genus-$0$ algebraic BRST/bar \textbf{proved}.
 (3)~$D^{\mathrm{co}}$-level BV=bar \textbf{proved} for all shadow classes.
 (4)~Chain-level BV/BRST/bar \textbf{proved} on the pro-object / $J$-adic /
 filtered weight-completed presentations of the raw bar complex; the bounded
 direct-sum ambient $\mathrm{Ch}(\mathrm{Vect})$ fails in class~M.
 (5)~Tree-level amplitude pairing \textbf{conditional}. &
 Thms~\ref{thm:general-hs-sewing},
 \ref{thm:algebraic-string-dictionary},
 \ref{thm:bv-bar-coderived-vol1} \\[4pt]

\textbf{Ambient $D^2 = 0$} &
At the ambient level (with planted-forest corrections),
$D^2 = 0$ is conditional on Mok's relative log-FM geometry together
with the manuscript's signed residue-pushforward construction. &
Thm~\ref{thm:ambient-d-squared-zero} \\[4pt]

\textbf{All-degree convergence} &
 The full shadow obstruction tower converges:
 $\Theta_\cA = \varprojlim \Theta_\cA^{\le r}$ exists. &
 Thm~\ref{thm:recursive-existence} \\[4pt]

\textbf{$\Eone$ A--H} &
Ordered ($\Eone$) fixed-curve and algebraic cores are proved where
stated; modular-family, planar planted-forest, and relative log-FM
extensions remain conditional on the same residue and gluing hypotheses. &
Thms~\ref{thm:e1-theorem-A-modular}--\ref{thm:e1-theorem-H-modular} \\[4pt]
\end{longtable}

\subsection*{Modular-completion comparison}

MC1 through MC4 are proved. MC5 is proved analytically/coderived and
on the strict Mittag--Leffler pro-object / $J$-adic / filtered
weight-completed chain surface. Analytic HS-sewing is established at all genera
(Theorem~\ref{thm:general-hs-sewing}); at genus~$0$ the algebraic
BRST/bar comparison is proved
(Theorem~\ref{thm:algebraic-string-dictionary}); the genuswise
BV/BRST/bar comparison on these completed/pro ambients is proved
\textup{(}Theorems~\ref{thm:mc5-class-m-chain-level-pro-ambient},
\ref{thm:mc5-class-m-topological-chain-level-j-adic};
Proposition~\ref{prop:ambient-equivalence}\textup{)}; the bounded
direct-sum ambient $\mathrm{Ch}(\mathrm{Vect})$ fails in class~$M$
already at weight~$4$; and the separate tree-level amplitude pairing is
conditional on Corollary~\ref{cor:string-amplitude-genus0}. MC3 is proved for all
simple types on the evaluation-generated core; the extension beyond
evaluation modules is not part of the proved MC3 core.
\begin{enumerate}[label=\textbf{MC\arabic*},leftmargin=3em]
\item \textbf{PBW concentration}: proved for all standard families
 (Proposition~\ref{prop:pbw-universality}).
\item \textbf{Bar-intrinsic MC element}: $\Theta_\cA := D_\cA - \dzero$
 is automatically MC because $D_\cA^2 = 0$
 (Theorem~\ref{thm:mc2-bar-intrinsic}).
\item \textbf{All-types MC3 reduction}: categorical prefundamental
 Clebsch--Gordan closure and the DK comparison on the
 evaluation-generated core are proved for all simple Lie types
 (Corollary~\ref{cor:mc3-all-types}).
\item \textbf{Completion towers}: strong completion-tower theorem
 (Theorem~\ref{thm:completed-bar-cobar-strong}).
 MC4 splits into MC4$^+$ (positive towers, solved) and
 MC4$^0$ (resonant towers, reduced to finite resonance).
\item \textbf{Sewing at all genera}: general HS-sewing criterion
 (Theorem~\ref{thm:general-hs-sewing}).
\end{enumerate}

\subsection*{The shadow obstruction tower}

The universal MC element $\Theta_\cA$ has finite-order
projections $\Theta_\cA^{\le r}$, each a graph sum through
degree~$r$ with obstruction class
$\mathfrak{o}_{r+1}(\cA) \in \mathrm{Def}_{\mathrm{cyc}}^{\mathrm{mod}}(\cA)$.
The named shadows are:
\[
\underbrace{\kappa}_{\text{degree 2}}
\;\to\;
\underbrace{C}_{\text{degree 3}}
\;\to\;
\underbrace{Q}_{\text{degree 4}}
\;\to\; \cdots
\]
Shadow depth classifies complexity within the Koszul world:
class~G ($r_{\max} = 2$, Heisenberg), class~L ($r_{\max} = 3$,
affine), class~C ($r_{\max} = 4$, $\beta\gamma$), class~M
($r_{\max} = \infty$, Virasoro/$\cW_N$). The full tower
$\Theta_\cA = \varprojlim \Theta_\cA^{\le r}$ converges
(Theorem~\ref{thm:recursive-existence}).

\subsection*{Dependency structure}

Logical dependencies:
\begin{center}
\begin{tikzcd}[column sep=small, row sep=small]
 \Theta_\cA^{\mathrm{ord}} \ar[r,"\mathrm{av}"] \ar[d,"\pi_{\mathrm{sc}}"']
 & \Theta_\cA \ar[d,"\pi_{\mathrm{sc}}"] \\
 \text{D} \ar[r,dashed] & \text{C}_{\mathrm{scalar}} \\
 \text{A} \ar[r] \ar[ur,dashed] & \text{B} \ar[u,dashed] \ar[ul,dashed] \\
 & \text{H} \ar[u,dashed]
\end{tikzcd}
\end{center}
The ordered MC element is constructed before averaging; its scalar
projection gives the diagonal part of Theorem~D. Theorem~A supplies the
bar--cobar adjunction and, on the Koszul locus, the Verdier route to
$\cA^!_\infty$. Theorem~B uses that adjunction plus Koszul or
completed Mittag--Leffler hypotheses to recover $\cA$ from
$\Omega\barB(\cA)$. Theorem~C has a Verdier/Lagrangian part independent
of the scalar genus formula and a scalar complementarity part whose
$\kappa+\kappa^!$ values use Theorem~D and the landscape census.
Theorem~H uses the chiral Hochschild spectral sequence together with
the Koszul bar--cobar comparison; it is independent of topological and
categorical Hochschild theories, not independent of the bar--cobar
surface.

\subsection*{Local algebra, deformation control, collision geometry}
\label{sec:guide-three-pillars}
\index{three-pillar architecture|textbf}

The MC equation
$D\cdot\Theta_\cA + \tfrac{1}{2}[\Theta_\cA,\Theta_\cA] = 0$
has three inputs: a homotopy chiral algebra on the curve, a filtered
convolution $sL_\infty$-algebra controlling twisting morphisms, and
logarithmic Fulton--MacPherson collision geometry.

\begin{enumerate}[label=\textup{(\Alph*)}]
\item \textbf{Local algebraic object.} The primitive local
 object is a \emph{homotopy chiral algebra}
 ($\mathrm{Ch}_\infty$-algebra) in the sense of
 Malikov--Schechtman~\cite{MS24}, not a strict chiral algebra. A strict
 chiral algebra appears only after rectification or on cohomology.

\item \textbf{Deformation-control object.} The deformation complex is a
 \emph{filtered convolution $sL_\infty$-algebra}
 $\operatorname{hom}_\alpha(\cC, \cA)$ relative to a twisting morphism
 $\alpha$, in the sense of Robert-Nicoud--Wierstra~\cite{RNW19} and
 Vallette~\cite{Val16}. The dg~Lie algebra $\gAmod$ of
 Definition~\ref{def:modular-convolution-dg-lie} is the strict model.
 \emph{Design constraint}:
 $\operatorname{hom}_\alpha$ extends to $\infty$-morphisms in either
 slot separately but not both simultaneously~\cite[Section~6]{RNW19}.

\item \textbf{Global collision geometry.} The natural
 compactification for punctured curves and nodal degenerations
 is \emph{logarithmic Fulton--MacPherson}
 $\overline{\operatorname{FM}}_n(X|D)$ on simple normal crossings pairs
 $(X, D)$, in the sense of Mok~\cite{Mok25}. Ordinary FM
 compactification is the special case $D = \emptyset$.
\end{enumerate}

\subsection*{Family index theorem}

\begin{theorem}[Family index theorem for genus expansions;
\ClaimStatusConditional]\label{thm:guide-family-index}
\index{index theorem!modular deformation|textbf}
\index{Grothendieck--Riemann--Roch!genus expansion|textbf}
Let $\cA$ be a Koszul chiral algebra with obstruction coefficient
$\kappa(\cA)$, let $\pi \colon \overline{\mathcal{C}}_g \to
\overline{\mathcal{M}}_g$ be the universal curve with relative
dualizing sheaf~$\omega_\pi$, and let
$\mathbb{E} = R^0\pi_*\omega_\pi$ be the Hodge bundle.
The following holds for uniform-weight modular Koszul algebras
at all genera; the genus-$1$ statements are unconditional for
all families.
The scalar deformation class is
\[
\mathcal{D}_{\cA}^{(g)}
:=
\kappa(\cA)\cdot\mathbb{E}
\in K_0(\overline{\mathcal M}_g)\otimes_{\mathbb Z}\mathbb Q .
\]
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{GRR formula.}
For uniform-weight algebras, the genus-$g$ free energy is the
GRR pushforward:
\[
F_g(\cA)
\;=\;
\kappa(\cA) \cdot
\int_{\overline{\mathcal{M}}_{g,1}} \psi^{2g-2}\, c_g(\mathbb{E}).
\]

\item \emph{$\hat{A}$-genus identification.}
The total generating function is
\[
\sum_{g \geq 1} F_g(\cA)\, x^{2g}
\;=\;
\kappa(\cA) \cdot \bigl(\hat{A}(ix) - 1\bigr)
\;=\;
\kappa(\cA) \cdot
\left(\frac{x/2}{\sin(x/2)} - 1\right).
\]

\item \emph{Verdier compatibility.}
Under the scalar Verdier partner $\cA^!$, the same GRR computation
applies with $\kappa(\cA^!)\cdot\mathbb{E}$. Hence any proved
complementarity value
\[
K^\kappa(\cA,\cA^!)=\kappa(\cA)+\kappa(\cA^!)
\]
gives
\[
\sum_{g\ge1}\bigl(F_g(\cA)+F_g(\cA^!)\bigr)x^{2g}
=K^\kappa(\cA,\cA^!)\bigl(\hat{A}(ix)-1\bigr)
\]
on the same uniform-weight scalar-diagonal lane. The values
$0,13,250/3,98/3$ and the Vol~III Mukai value $8$ are supplied by
Theorem~\ref{thm:derived-centre-complementarity-strengthened} and
Convention~\ref{conv:theorem-c-bucket}; they are not consequences of
GRR alone.
\end{enumerate}
\end{theorem}

\subsection*{The K3 paramodular object}
\label{sec:guide-k3-master-object}
\index{K3 chiral bialgebra!paramodular object|textbf}
\index{Delta_5@$\Delta_5$!Quillen norm|textbf}

The K3 base point supplies a paramodular comparison object for the
Theorem~C scalar bucket and the genus-one determinant lane. Write
$\mathfrak g_{\Delta_5} = \mathrm{Borch}(F_3,\phi^{K3}_{0,1})$ for
the K3-BKM Lie superalgebra produced by Borcherds lift from the
hyperbolic lattice $\Lambda_{\mathrm{Muk},II}^{2,1}$ (rank-$3$
hyperbolic core orthogonal to rank-$24$ Mukai), and let
$\mathbf H_{\Delta_5}$ be its non-abelian K3 chiral bialgebra
realisation. The Weyl denominator is the Gritsenko paramodular
weight-$5$ cusp form $\Delta_5 \in S_5(K(1))$.

\begin{theorem}[K3 paramodular L-value identity;
 \ClaimStatusProvedElsewhere]\label{thm:guide-k3-master-L-value}
\index{paramodular L-value!K3|textbf}
The genus-$1$ free energy of $\mathbf H_{\Delta_5}$ factors as
\[
\log Z^{(1)}_{\mathbf H_{\Delta_5}}
\;=\;-\log\bigl\|\Delta_5\bigr\|^2_{\mathrm{Quillen}}
\;=\;-\log\Delta_5 \;-\; \kappa_{\mathrm{BGS}}\,
L'\bigl(0,\Delta_5,\mathrm{std}\bigr),
\qquad
\kappa_{\mathrm{BGS}} \;=\; 24 \;=\; \chi_{\mathrm{top}}(K3),
\]
via Bruinier--K\"uhn~$2003$ composed with Bismut--Gillet--Soul\'e~$1988$.
The $L$-function is \emph{standard}, not adjoint-spinor: Pitale--Saha--Schmidt~$2014$
CAP factorisation together with the Waldspurger squaring rule rules
out $L'(0,\Delta_{10},\mathrm{ad}^0)$ as a candidate.
\end{theorem}

\begin{remark}[Four sibling functors over $\overline{\mathcal A_2}$]
\label{rem:guide-four-siblings}
\index{sibling functors!paramodular quadrichotomy|textbf}
The Baily--Borel--Freitag stratification of the Siegel
compactification $\overline{\mathcal A_2}$ carves
$\mathbf H_{\Delta_5}$ into four sibling functors
$\{\Psi,\Psi^{\deg},\Psi^{\mathrm{tor}},\Psi^{\mathrm{metap}}\}$
indexed by reflective interior, Klingen cusp (super-affine),
Humbert divisor (quantum-toroidal), and metaplectic branch
(Conway $V^{s\natural}$). The Humbert divisor is the
Argyres--Douglas locus of the class-$\mathcal S$ SCFT
$\mathcal T[A_1,\Sigma_{0,24}]$: at $E_{\tau_1}\times E_{\tau_2}$
the Seiberg--Witten curve degenerates to $(A_1,A_{2N-1})$
(Gaiotto--Moore--Neitzke~$2009$, Example~$8.3$). The four-archetype
quadrichotomy $G/L/C/M$ is the averaging shadow of this paramodular
quadrichotomy; the $FF$ companion is the critical-level degeneration
of the reflective interior.
\end{remark}

\begin{remark}[Humbert--Heegner admissibility filtration]
\label{rem:guide-humbert-heegner}
\index{Humbert--Heegner!admissibility filtration|textbf}
The pentagon tower $\{\phi^{(n)}\}_{n\ge 3}$ on the K3 chiral
bialgebra satisfies
\[
\phi^{(n)} \;=\; 0
\qquad\text{unless}\qquad
n \;\equiv\; 3,5 \pmod 8,
\]
equivalently $D_n = (n-3)/2 \in \{0,1\}\pmod 4$. The first admissible
nonvanishing rung is $\phi^{(5)} = -2\cdot [\mathrm{gen}]^{\otimes 5}$,
producing the depth reduction used on the K3 lane without invoking
Zagier--Hoffman regularisation.
\end{remark}

\begin{remark}[Bloch--Kato Selmer deformation and metaplectic $\mathrm{grt}_1^{(1/2)}$]
\label{rem:guide-selmer-metaplectic}
\index{Bloch--Kato Selmer!$\Delta_5$|textbf}
\index{metaplectic Grothendieck--Teichm\"uller!$\mathrm{grt}_1^{(1/2)}$|textbf}
The arithmetic enhancement of the K3 chiral bialgebra is conjectural.
It predicts a one-dimensional cyclotomic-paramodular Hida deformation
of $\mathbf H_{\Delta_5}$:
\[
\dim H^1_f\bigl(\mathbb Q,\,\mathrm{std}\,\rho_{\Delta_5}\bigr)
\;=\; 1
\qquad\text{(Bloch--Kato prediction)},
\]
and it predicts that the Grothendieck--Teichm\"uller torsor action on
$\mathrm{Face}(\cA)$ lifts to a metaplectic non-split extension
$\mathrm{grt}_1^{(1/2)} \twoheadrightarrow \mathrm{grt}_1$ by
even-weight generators carrying Saito--Kurokawa motivic content,
with fundamental bracket
\[
[\widetilde\sigma_2,\widetilde\sigma_2] \;=\; 288\,\widetilde\sigma_4,
\qquad
288 \;=\; \tau(2)^2/2,
\]
(Ramanujan tau at $2$, squared and halved).
\end{remark}

\begin{remark}[Chiral-Hochschild $W_\infty\lbrack c=-214\rbrack$ cocycles]
\label{rem:guide-hochschild-cocycles}
\index{chiral Hochschild cocycles|textbf}
The chiral-Hochschild cocycles $e_3,e_4,e_5,e_6$ at the
$W_\infty[c=-214]$ base point admit explicit descriptions: by
Wang~$1998$ Proposition~$4.2$, $e_5 = W_5$ identically; the
quartic refines to $e_4 = W_4 - (107/11)\,\Lambda_Z$ with
$\Lambda_Z$ the normal-ordered Zamolodchikov quasi-primary. Together
with Remark~\ref{rem:guide-humbert-heegner} and
Theorem~\ref{thm:guide-k3-master-L-value} these pin the arithmetic
shape of the $\mathbf H_{\Delta_5}$ derived centre.
\end{remark}

\subsection*{Structural principles}

\begin{principle}[Gravitational primitivity]
\label{princ:guide-gravitational-primitivity}
\index{coproduct!gravitational primitivity|textbf}
For any principal Drinfeld--Sokolov reduction
$W_k(\fg) = H^0_{\mathrm{BRST}}(\widehat{\fg}_k, f_{\mathrm{prin}})$,
the HPL-transferred coproduct is strictly primitive at all degrees:
$\Delta_{z,n}^W = 0$ for all $n \ge 2$.
All nontrivial structure of the transferred dg-shifted Yangian
resides in the $\Ainf$ products $\{m_n^W\}_{n \ge 3}$ and in
the collision residue $r(z)$. The mechanism is a ghost-number
obstruction intrinsic to DS reduction.
\end{principle}

\begin{remark}[Four modular tests]
\label{rem:guide-four-test-interface}
\ClaimStatusConditional
\index{four modular tests|textbf}
The modular Koszul comparison with $\overline{\mathcal{M}}_{g,n}$ is
controlled by four tests, each with its own hypotheses:
\textup{(1)}~$D_\cA^2 = 0$ at all genera and degrees
\textup{(}Theorems~\textup{\ref{thm:bar-modular-operad},
\ref{thm:quantum-diff-squares-zero}}\textup{)};
\textup{(2)}~$\mathrm{obs}_g(\cA) = \kappa(\cA)\cdot\lambda_g$
\textup{(}UNIFORM-WEIGHT\textup{})
for uniform-weight algebras at all genera,
unconditionally at genus~$1$
\textup{(}Theorem~\textup{\ref{thm:modular-characteristic}}\textup{)};
\textup{(3)}~$Q_g(\cA)+Q_g(\cA^!)=H^*(\overline{\mathcal M}_g,\cZ_\cA)$:
complementarity assembles the Koszul pair into a Lagrangian
decomposition
\textup{(}Theorem~\textup{\ref{thm:quantum-complementarity-main}}\textup{)};
\textup{(4)}~sewing: genus-$g$ amplitudes converge from lower-genus data
\textup{(}Theorem~\textup{\ref{thm:general-hs-sewing}}\textup{)}.
\end{remark}

\subsection*{The four-test boundary of control}
\label{subsec:guide-four-test-boundary}
\index{boundary of control|textbf}

Inside the modular Koszul locus the algebraic comparison is governed
by Koszulness, scalar-diagonal weight behaviour, analytic sewing, and
algebraicity of the family. Crossing a wall of non-Koszulness,
non-scalar-diagonal weights, non-convergence, or non-algebraicity
requires an additional theorem; none of the four walls is crossed by
formal bar--cobar adjunction alone.

\subsection*{Factorization-envelope technology}
\label{sec:guide-nishinaka-vicedo}
\index{factorization envelope!Lie conformal|textbf}

The Nishinaka~\cite{Nishinaka25} and
Vicedo~\cite{Vicedo25} constructions provide a functorial passage from
Lie conformal algebras to factorization algebras
and vertex algebras. Starting from a Lie conformal algebra~$R$,
the factorization envelope $\operatorname{Fact}(R)$ produces the
enveloping vertex algebra $U^{\mathrm{vert}}(R)$, which carries
the bar complex and the full shadow obstruction tower. The
\emph{envelope-shadow functor}
$\Theta^{\mathrm{env}}(R):=\Theta(U^{\mathrm{vert}}(R))$ is a functorial
source of shadow towers on Lie conformal input.

\subsection*{Modular cooperad completion}
\label{sec:concordance-modular-cooperad-completion}
\index{modular cooperad!completion|textbf}

The modular completion of the bar coalgebra extends the genus-$0$
factorization coalgebra structure to all genera via the modular
operad. The sewing amplitudes at genus~$g$ are the compositional
structure maps of the completed modular cooperad
$\barB^{\mathrm{mod}}(\cA)$.

\subsection*{Scalar and operadic separations}
\label{sec:guide-architectural-sharpenings}

The scalar, operadic, and arithmetic lanes are distinct.

\smallskip\noindent\emph{Scalar conductors.}
There are four adjacent scalars, not one:
\[
K_E(A)=\chi(\barB_X(A)),\qquad
K^c(A,A^!)=c(A)+c(A^!),\qquad
K^\kappa(A,A^!)=\kappa(A)+\kappa(A^!),\qquad
K_{\mathrm{ghost}}^{\mathrm{leg}}(A)
=-c_{\mathrm{ghost}}(\mathrm{BRST}_{\mathrm{can}}(A)).
\]
Theorem~C uses $K^\kappa$. The central-charge sum $K^c$ and the ghost
scalar $K_{\mathrm{ghost}}^{\mathrm{leg}}$ require their own witness
lanes. Equality among these scalars is a theorem on a specified
standard witness, not a formal consequence of bar--cobar duality.

\smallskip\noindent\emph{Chain homotopies.}
The bar--cobar homotopies used in Theorem~A are constructed in the
conilpotent or completed bar--cobar ambient. No universal formula
$h_\cA=h_{\mathrm{LV}}/(\kappa+\kappa^!)$ is used: $K^\kappa$ may
vanish on the Heisenberg, affine, and free-field scalar lanes, while
the adjunction and inversion statements still make sense in their
proper ambients.

\smallskip\noindent\emph{Shadow tower constants.}
Closed Virasoro shadow coefficients are read from
Chapter~\ref{chap:shadow-tower-higher-coefficients} in the chosen
normalisation. In particular
\[
S_2=c/2,\qquad S_3=2,\qquad
S_4=\frac{10}{c(5c+22)},\qquad
S_5=-\frac{48}{c^2(5c+22)},
\]
and the null-state normalisation gives
\[
S_6(\Vir_c)=\frac{4(240c+1031)}{c^3(5c+22)^2}.
\]
Metric/Stokes quantities such as $|\omega|^2(c)$ belong to the
Riccati-metric lane and are not substitutes for the $S_r$ coefficients.

\smallskip\noindent\emph{Arithmetic shadow.}
The congruence
\[
\det\rho_{S_{11}(V_1(\mathfrak g)),\,691}
 = \chi_{\mathrm{cyc}}^{11}\cdot\varepsilon_{B_{12}}\pmod{691}
\]
is an arithmetic-shadow statement via Kubota--Leopoldt and
Herbrand--Ribet. It does not determine $K^\kappa$, $K^c$, or the ghost
scalar.

\smallskip\noindent\emph{Drinfeld double.}
$\mathrm{obs}^{(1)}_{\mathrm{double}}\in
H^2(\mathfrak{grt}^{\mathrm{ell}},\mathfrak{sp}(\cA)\otimes\mathfrak{sp}(\cA^!))$
vanishes iff $r_{\max}(\cA)=2$.

\smallskip\noindent\emph{Three-lane averaging.} Chain-level averaging
is defined on the ordered bar complex. The $R$-twisted plethystic lane
requires $C_2$-cofinite, non-logarithmic, non-critical hypotheses. The
Boltzmann-to-Bose comparison is proved only on class~$\mathsf G$.

\smallskip\noindent\emph{Two-stage CY functor.}
$\Phi_d = \mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}\circ\Phi^{\mathrm{FA}}_d$
with Stage-1 formal locus, PTVV-forced native level
$d=1\Rightarrow n=\infty$, $d=2\Rightarrow n=2$, $d\ge 3\Rightarrow n=1$.

\smallskip\noindent\emph{Eight-form spread.} Weights
$\{5,2,1,1,1/2,1,1/4,0\}$, zero-coefficients
$\{10,4,2,2,1,2,1/2,0\}$, universal Borcherds-weight identity
$\kappa_{\mathrm{BKM}}(\Phi_N)=c_N(0)/2$;
$\mathrm{Sp}_4/\mathrm{Mp}_4/\widetilde{\mathrm{Mp}}_4$ covers by
weight parity.

\smallskip\noindent\emph{Three-tier topologisation.} Tier~I
cohomological and Tier~II chain-level on qi-model unconditional;
Tier~III strict original-complex closed for $\mathsf G,\mathsf L,\mathsf C$,
open for $\mathsf M$ on the strict original-complex lane.

\smallskip\noindent\emph{Boundary problems.}
The theorem surfaces above leave the following hypotheses or
constructions outside their proved ambients:
$\cW(p)$ tempering; periodic CDG non-simply-laced comparison;
Tier~III class~$\mathsf M$ strict original-complex topologisation;
super-complementarity pairing; irregular KZB and the Drinfeld-double
obstruction; nodal Theorem~B; MC4 resonance completion; Stage~1 at
$d\ge4$; categorical $E_d$-formality at $d\ge4$; bracket-level BPS Lie
algebra on $K3\times E$.

\subsection*{Notation}

$\barB$: bar functor. $\Omega$: cobar functor.
$\cA^!$: Koszul dual.
$\kappa(\cA)$: modular characteristic.
$Q_g(\cA)$: genus-$g$ partition complex.
$\ChirHoch^*$: chiral Hochschild cohomology.
$\gAmod$: modular convolution dg~Lie algebra.
$\Theta_\cA$: universal MC element.
$\Eone$, $\Einf$: associative and commutative operadic levels.
$\FM_n(X)$: Fulton--MacPherson compactification.
