\chapter{Introduction}\label{ch:heisenberg-frame}

We begin not with an abstraction but with an atom.
The Heisenberg algebra $\mathcal{H}_k$ is the place where the
governing object of this monograph---the universal Maurer--Cartan
element $\Theta_\cA \in \MC(\mathfrak{g}_\cA^{\mathrm{mod}})$---can
be seen in one glance, because in the abelian case
$\Theta_{\mathcal{H}_k}$ collapses to a \emph{scalar}: the single
number $\kappa(\mathcal{H}_k) = k$ determines the bar complex (Arnold
relation forces $d^2 = 0$), the Koszul dual (Verdier duality on FM
compactifications), the genus tower ($\kappa \cdot \hat{A}$-genus),
and the complementarity that balances quantum corrections against their
duals---all projections of one MC element computable by hand on a
single generator with a double pole.
The cubic shadow vanishes, the quartic contact invariant vanishes, and
the entire shadow Postnikov tower terminates at weight~$2$.  That
collapse is itself instructive: it is the \emph{Gaussian archetype},
where the MC element has no nonlinear obstructions and the genus
expansion closes in one step.

The strategy of the volume is: example first, theory after.  Every
theorem proved in Part~I will be instantiated here before it is stated
in generality.  The reader who works through this chapter with pencil
in hand---writing out the Arnold relation for three points,
differentiating the bar complex at degree~$2$, checking that the
Bernoulli numbers appear in the genus expansion---will have seen the
entire machine operate on the simplest possible input.  The purpose of
the rest of the monograph is to explain why it still works when the
input is no longer simple: when the OPE has simple poles as well as
double poles, when the algebra is nonabelian, when the genus is
positive, and when the shadows no longer terminate.

Think of $\Theta_{\mathcal{H}_k} = k \cdot \eta \otimes \Lambda$ as a
Steinberg-variety moment in the sense of geometric representation
theory: a fixed point whose structure already encodes the geometry of
the full flag variety.  Just as the Springer resolution is visible
from a single nilpotent orbit, the entire modular convolution algebra
$\mathfrak{g}_\cA^{\mathrm{mod}}$ and its MC moduli are visible from
the single current $\alpha(z)$ and its double-pole OPE---because the
Heisenberg MC element is scalar, so every projection (bar complex,
Koszul dual, genus tower, complementarity) is a single number times a
universal form.
The passage from this chapter to Part~I is the passage from the scalar
MC element to the full nonlinear $\Theta_\cA$, where the shadow tower
no longer terminates and the MC moduli acquires genuine geometry.

The Heisenberg algebra is the minimal commutative atom that already
displays the full modular bar-cobar mechanism in computable form: the
bar differential can be written down explicitly, Verdier duality is
visible without auxiliary generators, the genus-$1$ defect is scalar,
and the genus tower closes to the $\hat{A}$-series.  What Heisenberg
cannot see is ordered factorization: there is no nontrivial braid
reversal and no $R$-matrix to invert.  That omission is structural.
The Yangian supplies the first genuinely braided example on the
$\Eone$ side.

The subject of this monograph is the bar construction for chiral
algebras on algebraic curves.  The starting point is a simple geometric
observation: place elements $a_1, \ldots, a_n$ of a chiral
algebra~$\cA$ at points $z_1, \ldots, z_n$ on a smooth curve~$X$,
extract residues of the operator product expansion along the boundary
divisors of the Fulton--MacPherson compactification~$\overline{C}_n(X)$,
and assemble the results into a graded coalgebra $\barB(\cA)$.  The
Arnold relation among triple collisions forces $d^2 = 0$: the bar
complex is a factorization coalgebra on $\Ran(X)$.

This construction, carried out for every major family of chiral algebras
--- Heisenberg, free fermions, $\beta\gamma$ systems, affine Kac--Moody
at arbitrary level, Virasoro, principal $\mathcal{W}$-algebras,
lattice vertex algebras, Yangians --- is the engine of chiral Koszul
duality.  The bar construction is the \emph{categorical logarithm}: its
kernel is the logarithmic form $\eta_{ij} = d\log(z_i - z_j)$, and it
maps the multiplicative OPE structure to the nilpotent bar differential
with $d^2 = 0$.  At genus~$0$, this logarithm is single-valued and
specializes to classical operadic Koszul duality.

At genus $g \geq 1$,
the logarithm acquires monodromy from the period structure of the curve,
the propagator acquires corrections from the Hodge bundle
over~$\overline{\mathcal{M}}_g$, the bar differential develops curvature
$\dfib^{\,2} = \kappa(\cA)\cdot\omega_g$ whose coefficient
$\kappa(\cA)$ is the infinitesimal generator of this monodromy, and the
genus tower organizes into a modular deformation whose generating
function is the $\hat{A}$-genus.  Throughout, \emph{nilpotence is the
logarithm of periodicity}: the nilpotent data ($d^2 = 0$, $\kappa$, the
bar differential) determine the periodic data (modular transformations,
periodicity of bar cohomology, the monodromy representation) via
exponentiation (Remark~\ref{rem:nilpotence-periodicity}).

The examples are arranged so that the geometry appears before its
braided refinement.  The first four examples stay on the commutative
$\Einf$ face, where unordered configurations, curvature, and
complementarity are already visible.  The lattice and Yangian previews
are included to show where that picture stops being sufficient: once
ordering becomes mathematical data, one leaves the Heisenberg world and
enters the braided $\Eone$ face.

\begin{itemize}
\item The \textbf{Heisenberg algebra}~$\mathcal{H}_k$
  (\S\ref{sec:frame-bar-deg1}--\S\ref{sec:frame-complementarity})
  carries the full vertical structure: the bar complex at genus~$0$,
  the Arnold relation, the Koszul dual, bar-cobar inversion, genus-$1$
  curvature, the $\hat{A}$-genus generating function, and the
  complementarity of quantum corrections.  Every theorem of Part~I is
  instantiated here.

\item \textbf{Free fermions and the $\beta\gamma$ system}
  (\S\ref{sec:frame-free-fields}) exhibit the Lie--Com duality of
  chiral algebras: the fermion, governed by a simple pole, is Koszul
  dual to the $\beta\gamma$ system.  This is the chiral incarnation
  of the classical $\mathrm{Lie}^! = \mathrm{Com}$ duality, and it
  clarifies the distinction between Koszul duality, bosonization, and
  level-shifting.

\item \textbf{Affine Kac--Moody algebras}
  (\S\ref{sec:frame-nonabelian-preview}) introduce both simple and
  double poles.  The bar differential acquires a bracket component
  from the simple pole and a curvature component from the double pole;
  neither is individually a differential.  The Borcherds identity,
  coupling both pole orders, replaces the Jacobi identity.  The PBW
  spectral sequence emerges as the correct computational tool, and
  the Feigin--Frenkel involution
  $k \leftrightarrow -k - 2h^\vee$ is revealed as Koszul duality.

\item \textbf{$\mathcal{W}$-algebras}
  (\S\ref{sec:frame-w-algebras}) arise from Kac--Moody via
  Drinfeld--Sokolov reduction and test the theory against derived
  constructions.  Composite fields such as
  $\Lambda = :\!TT\!: - \tfrac{3}{10}\partial^2 T$ introduce
  quartic OPE poles; the PBW spectral sequence does not automatically
  degenerate.  Koszul duality commutes with DS reduction, extending
  the Feigin--Frenkel involution to the full $\mathcal{W}$-algebra
  tower.

\item \textbf{Lattice vertex algebras}
  (\S\ref{sec:frame-yangian-preview}) bring $\Eone$-monoidal
  structure from the braiding.  Cocycle deformations produce quantum
  lattice algebras, and the $\Eone$ bar-cobar adjunction inverts
  the quantum parameter: $\varepsilon \mapsto \varepsilon^{-1}$.

\item \textbf{Yangians} (\S\ref{sec:frame-yangian-preview}) realize
  the $R \leftrightarrow R^{-1}$ duality in factorization form.
  Through factorization homology, the chiral Koszul duality of the
  Yangian recovers the Drinfeld--Kohno equivalence between KZ
  monodromy and quantum group representations.
\end{itemize}

\begin{remark}[The four theorems for Heisenberg]%
\label{rem:frame-governing-picture}
This chapter instantiates all four main theorems for~$\mathcal{H}_k$:
\textbf{A}~(\S\ref{sec:frame-koszul-dual}): $\mathcal{H}_k^! = (\mathrm{Sym}^{\mathrm{ch}}(V^*), m_0 = -k\omega)$.
\textbf{B}~(\S\ref{sec:frame-inversion}): $\Omega\barB(\mathcal{H}_k) \xrightarrow{\sim} \mathcal{H}_k$.
\textbf{C}~(\S\ref{sec:frame-complementarity}): $Q_g(\mathcal{H}_k) \oplus Q_g(\mathcal{H}_k^!) = H^*(\overline{\mathcal{M}}_g, \mathcal{Z}_{\mathcal{H}_k})$.
\textbf{D}~(\S\ref{sec:frame-genus-tower}): $\kappa(\mathcal{H}_k) = k$; $\sum_{g \geq 1} F_g\, x^{2g} = k(\tfrac{x/2}{\sin(x/2)} - 1)$.
\end{remark}

\medskip

We begin with the Heisenberg algebra, the smallest $\Einf$-chiral
algebra in which every load-bearing phenomenon on the
commutative/modular face of this monograph is already forced.

Let $X$ be a smooth algebraic curve.  The Heisenberg chiral algebra
$\mathcal{H}_k$ at level $k \in \mathbb{C}^\times$ has a single current
$\alpha(z)$ of conformal weight~$1$, with operator product expansion
\begin{equation}\label{eq:frame-heisenberg-ope}
\alpha(z)\alpha(w) = \frac{k}{(z-w)^2} + \text{regular}.
\end{equation}
The double pole is the entire structure.  In mode expansion,
$\alpha(z) = \sum_{n \in \mathbb{Z}} \alpha_n z^{-n-1}$, and the
commutation relations are
\begin{equation}\label{eq:frame-heisenberg-modes}
[\alpha_m, \alpha_n] = k \cdot m \cdot \delta_{m+n,0}.
\end{equation}
The vacuum representation (Fock space) is
$\mathcal{F}_k = \mathbb{C}[\alpha_{-1}, \alpha_{-2}, \ldots]\,|0\rangle$
with $\alpha_n|0\rangle = 0$ for $n > 0$.  The Sugawara construction gives
the stress tensor $T = \frac{1}{2k}:\!\alpha(z)\alpha(z)\!:$ with central
charge $c = 1$.

The absence of a simple pole in the self-OPE is the defining feature.
Free fermions have a simple pole $\psi(z)\psi(w) \sim 1/(z-w)$; affine
Kac--Moody algebras $\widehat{\mathfrak{g}}_k$ have both simple and double
poles.  The Heisenberg algebra, with its double pole alone, isolates the
role of the curvature (double-pole) sector, free from the complications
of the bracket (simple-pole) sector.

\begin{remark}[Fourier identification]\label{rem:frame-fourier-identification}
The bar complex $\barB(\mathcal{H}_k)$ is the abelian one-dimensional
Fourier transform of the Heisenberg algebra
(Chapter~\ref{ch:fourier-seed}).  The $\hat{A}$-genus appearing in
Theorem~D (Theorem~\ref{thm:modular-characteristic}) is its
characteristic function---the analogue of $e^{-t|\xi|^2}$ for the
classical heat kernel.
\end{remark}

% ================================================================
\section{The bar complex at degree 1}\label{sec:frame-bar-deg1}
% ================================================================

The geometric bar complex of $\mathcal{H}_k$ on $X$ has underlying
graded space
\begin{equation}\label{eq:frame-bar-graded}
\bar{B}^{\mathrm{ch}}_n(\mathcal{H}_k) = \Gamma\!\left(
  \overline{C}_{n+1}(X),\;
  \alpha^{\boxtimes(n+1)} \otimes \Omega^n_{\log}
\right)
\end{equation}
where $\overline{C}_{n+1}(X)$ is the Fulton--MacPherson compactification
of the configuration space of $n+1$ distinct points on~$X$, and
$\Omega^n_{\log}$ denotes logarithmic $n$-forms along the boundary
divisors $D_{ij} = \{z_i = z_j\}$.

A typical element of $\bar{B}^{\mathrm{ch}}_1$ is
\begin{equation}\label{eq:frame-bar1-element}
\alpha(z_1) \otimes \alpha(z_2) \otimes \eta_{12}
\end{equation}
where
\begin{equation}\label{eq:frame-eta-def}
\eta_{ij} = d\log(z_i - z_j) = \frac{dz_i - dz_j}{z_i - z_j}
\end{equation}
is the logarithmic $1$-form associated to the diagonal
$D_{ij} \subset X \times X$.

The bar differential $d_{\mathrm{res}}$ extracts OPE data at boundary
divisors via the Borcherds identity.  We now give the full computation.

\subsubsection*{Grading and desuspension accounting}

The bar complex uses cohomological grading and desuspension.
The current $\alpha(z)$ has conformal weight~$|\alpha| = 1$.
Under desuspension, the bar complex element $s^{-1}\alpha$ has
cohomological degree shifted by~$+1$:
\begin{equation}\label{eq:frame-desuspension-shift}
\deg(s^{-1}\alpha) = |\alpha| + 1 = 2.
\end{equation}
A degree-$n$ bar element involves $(n+1)$ desuspended currents
and an $n$-form, giving total cohomological degree
\[
(n+1) \cdot \deg(s^{-1}\alpha) + \deg(\eta) = 2(n+1) + 0 = 2n + 2,
\]
where the logarithmic forms $\eta_{ij}$ carry form-degree~$1$ but
cohomological degree~$0$ in the bar complex grading.  The bar
differential has $|d_{\mathrm{res}}| = +1$ in cohomological degree.

For a degree-$1$ element, the data is:
\begin{align}
&\text{two desuspended currents:} \quad
  s^{-1}\alpha(z_1) \otimes s^{-1}\alpha(z_2),
  \label{eq:frame-deg1-currents} \\
&\text{one logarithmic $1$-form:} \quad
  \eta_{12} = \frac{dz_1 - dz_2}{z_1 - z_2}.
  \label{eq:frame-deg1-form}
\end{align}

\subsubsection*{Action of $d_{\mathrm{res}}$ at degree~$1$}

The bar differential acts by restriction to the boundary stratum
$D_{12} = \{z_1 = z_2\} \subset \overline{C}_2(X)$.  The mechanism
is the Borcherds identity: for fields $a(z), b(w)$ with OPE
$a(z)b(w) = \sum_{n \geq 1} c_n(w)/(z-w)^n + \mathrm{regular}$,
the bar differential extracts the OPE coefficients via
\begin{equation}\label{eq:frame-borcherds-extraction}
d_{\mathrm{res}}\bigl(
  s^{-1}a(z_1) \otimes s^{-1}b(z_2) \otimes \eta_{12}
\bigr)
= \sum_{n \geq 1} \frac{1}{(n-1)!}\,
  \partial_{z_2}^{n-1} c_n(z_2)\Big|_{z_1 = z_2}.
\end{equation}
The logarithmic form $\eta_{12}$ plays the role of a test
form for the boundary pairing on $D_{12}$, pairing with the
codimension-$1$ boundary stratum to extract the
residue data.

For the Heisenberg OPE~\eqref{eq:frame-heisenberg-ope},
the only pole is the double pole $c_2 = k$, with $c_1 = 0$
(no simple pole).  Therefore:
\begin{align}
d_{\mathrm{res}}\bigl(
  s^{-1}\alpha(z_1) \otimes s^{-1}\alpha(z_2) \otimes \eta_{12}
\bigr)
&= \frac{1}{(2-1)!}\,\partial_{z_2}^{2-1}(k)\Big|_{z_1 = z_2}
\notag \\
&= \partial_{z_2}(k) = 0
  \qquad\text{(na\"ive: }\partial\text{ of a constant)}
\label{eq:frame-dres-deg1-naive}
\end{align}
but this is \emph{not} the correct reading.  The Borcherds identity
for a second-order pole with constant coefficient gives directly
\begin{equation}\label{eq:frame-dres-deg1}
d_{\mathrm{res}}(\alpha(z_1) \otimes \alpha(z_2) \otimes \eta_{12})
= k \cdot 1
\end{equation}
extracting the second-order pole coefficient into the
degree-$0$ component $\bar{B}^{\mathrm{ch}}_0 = \mathbb{C}$.

\subsubsection*{The general degree-$1$ element}

More generally, let $f(z_1, z_2)$ be a test function (a section of
$\mathcal{O}_{X \times X}$ near the diagonal).  The general
degree-$1$ element is
\begin{equation}\label{eq:frame-deg1-general}
\xi = f(z_1, z_2) \cdot \alpha(z_1) \otimes \alpha(z_2)
  \otimes \eta_{12} \;\in\; \bar{B}^{\mathrm{ch}}_1.
\end{equation}
The bar differential restricts to $D_{12}$ and extracts:
\begin{align}
d_{\mathrm{res}}(\xi)
&= \mathrm{Res}_{D_{12}}\!\left[
  f(z_1, z_2) \cdot
  \frac{k}{(z_1 - z_2)^2} \cdot \eta_{12}
\right] \notag \\
&= k \cdot \partial_{z_1}\! f(z_1, z_2)\Big|_{z_1 = z_2}
  + k \cdot f(z, z) \cdot (\text{contact term}).
\label{eq:frame-dres-deg1-general}
\end{align}
For the standard element $f(z_1, z_2) = 1$, the derivative
vanishes and the contact term gives $k \cdot 1$, recovering
\eqref{eq:frame-dres-deg1}.  The derivative term
$k \cdot \partial_{z_1} f|_{\mathrm{diag}}$ is the
``descendant'' contribution: it appears only for non-constant
test functions and produces elements of the vacuum module.

A clarification is essential.  The bar differential does \emph{not} act
by literally computing
$\mathrm{Res}_{z_1 = z_2}[k/(z_1-z_2)^2 \cdot dz_1/(z_1-z_2)]$:
that integral involves a triple pole with zero residue.  The differential
$d_{\mathrm{res}}$ uses the Borcherds identity to extract the OPE
coefficient at the boundary stratum~$D_{12}$; the logarithmic form
$\eta_{12}$ serves as a test form for the boundary pairing, not as a
multiplicative factor in a meromorphic expression.

\begin{remark}[Where the OPE data goes]\label{rem:frame-ope-extraction}
The map $d_{\mathrm{res}}\colon \bar{B}^{\mathrm{ch}}_1 \to
\bar{B}^{\mathrm{ch}}_0 = \mathbb{C}$ sends each pair of currents
to the constant $k$.  On $\mathbb{P}^1$, where $H^1(X) = 0$, the
kernel of $d_{\mathrm{res}}$ on $\bar{B}_1$ is trivial: every element
maps to a nonzero multiple of the vacuum.  At higher genus, zero modes
of $\alpha(z)$ along cycles of $\Sigma_g$ contribute nontrivially to
$\ker(d_{\mathrm{res}})$, producing $H^1 \cong H^1(\Sigma_g, \mathbb{C})$
(Theorem~\ref{thm:heisenberg-higher-genus}).
\end{remark}

% ================================================================
\section{The bar complex at degree 2 --- Arnold enters}
\label{sec:frame-bar-deg2}
% ================================================================

The degree-$2$ bar complex $\bar{B}^{\mathrm{ch}}_2$ involves three
currents and two logarithmic forms:
\begin{equation}\label{eq:frame-bar2-element}
\alpha(z_1) \otimes \alpha(z_2) \otimes \alpha(z_3)
\otimes \eta_{12} \wedge \eta_{23}.
\end{equation}

\subsubsection*{Sign conventions for the bar differential at degree~$2$}

Before computing, we fix signs.  The bar differential is a sum over
boundary strata:
\begin{equation}\label{eq:frame-d-sum-strata}
d_{\mathrm{res}} = \sum_{1 \leq i < j \leq n+1}
  (-1)^{\sigma(i,j)}\, \partial_{D_{ij}}
\end{equation}
where $\partial_{D_{ij}}$ restricts to the divisor
$D_{ij} = \{z_i = z_j\}$ and extracts the OPE coefficient, and
$\sigma(i,j)$ is the Koszul sign arising from permuting the
desuspended elements past each other.

For degree-$2$ elements with three desuspended currents
$s^{-1}\alpha(z_1) \otimes s^{-1}\alpha(z_2) \otimes s^{-1}\alpha(z_3)$,
the Koszul sign rule gives the following.
Each desuspended current $s^{-1}\alpha$ has degree~$2$
(conformal weight $1$ plus desuspension shift $1$), hence
is \emph{even} in the graded sense.  Moving even-degree elements
past each other produces sign $(-1)^{2 \cdot 2} = +1$.
Consequently, for the Heisenberg algebra (single even generator),
\emph{all Koszul signs from the coalgebra coproduct are~$+1$}.
The signs in the bar differential come entirely from the
orientation of the logarithmic forms on the boundary strata.

\subsubsection*{Term-by-term computation of $d_{\mathrm{res}}$}

The element~\eqref{eq:frame-bar2-element} lives on
$\overline{C}_3(X)$, whose boundary divisors are $D_{12}$, $D_{23}$,
and $D_{13}$.  The bar differential restricts to each:

\medskip
\noindent\textbf{Boundary stratum $D_{12}$: collision $z_1 = z_2$.}
The OPE $\alpha(z_1)\alpha(z_2) = k/(z_1 - z_2)^2 + \mathrm{reg.}$
collapses the pair to the scalar~$k$.  The form
$\eta_{12} \wedge \eta_{23}$ restricts to $D_{12}$ by the rule:
$\eta_{12}$ is ``consumed'' by the boundary pairing
on~$D_{12}$ (it is the test form for this stratum), and the
residual form is $\eta_{23}|_{z_1 = z_2}$.  Since $z_1 = z_2$
on $D_{12}$, the residual form is simply $\eta_{23}$ (which
does not involve $z_1$, so it is unaffected by the collision).
The sign from the wedge product is $+1$ because $\eta_{12}$ is
the \emph{left} factor:
\begin{equation}\label{eq:frame-D12-contribution}
\partial_{D_{12}}\bigl(
  \alpha \otimes \alpha \otimes \alpha \otimes
  \eta_{12} \wedge \eta_{23}
\bigr)
= +k \cdot \alpha(z_3) \otimes \eta_{23}.
\end{equation}
Here $\alpha(z_3) \otimes \eta_{23}$ is a degree-$1$
element: a single surviving current with a single logarithmic
form, living on $\overline{C}_2(X)$ with coordinates $(z_{12}, z_3)$
where $z_{12}$ is the collision point.

\medskip
\noindent\textbf{Boundary stratum $D_{23}$: collision $z_2 = z_3$.}
The OPE $\alpha(z_2)\alpha(z_3) = k/(z_2 - z_3)^2 + \mathrm{reg.}$
collapses the pair to~$k$.  The form $\eta_{12} \wedge \eta_{23}$
restricts to $D_{23}$ by consuming $\eta_{23}$ (the test form
for this stratum).  To consume $\eta_{23}$, we must move it to
the left of $\eta_{12}$, producing a sign from the wedge:
\[
\eta_{12} \wedge \eta_{23} = -\eta_{23} \wedge \eta_{12}.
\]
The residual form after consuming $\eta_{23}$ is $\eta_{12}|_{z_2 = z_3}$.
On $D_{23}$, $z_2 = z_3$, so $\eta_{12}|_{z_2 = z_3} = \eta_{13}$
(the form $d\log(z_1 - z_2)$ becomes $d\log(z_1 - z_3)$
when $z_2 = z_3$).  The surviving current is $\alpha(z_1)$.
Including the sign from the wedge permutation:
\begin{equation}\label{eq:frame-D23-contribution}
\partial_{D_{23}}\bigl(
  \alpha \otimes \alpha \otimes \alpha \otimes
  \eta_{12} \wedge \eta_{23}
\bigr)
= -k \cdot \alpha(z_1) \otimes \eta_{13}.
\end{equation}

\medskip
\noindent\textbf{Boundary stratum $D_{13}$: collision $z_1 = z_3$.}
The OPE $\alpha(z_1)\alpha(z_3) = k/(z_1 - z_3)^2 + \mathrm{reg.}$
collapses the pair to~$k$.  However, the $2$-form
$\eta_{12} \wedge \eta_{23}$ does \emph{not} contain the
factor $\eta_{13}$ as a wedge component.  The restriction of
$\eta_{12} \wedge \eta_{23}$ to $D_{13}$ involves:
\[
\eta_{12}\big|_{z_1 = z_3} = \eta_{32}
= -\eta_{23}, \qquad
\eta_{23}\big|_{z_1 = z_3} = \eta_{23}.
\]
So $(\eta_{12} \wedge \eta_{23})|_{D_{13}}
= (-\eta_{23}) \wedge \eta_{23} = 0$.
The boundary stratum $D_{13}$ contributes \emph{zero}:
\begin{equation}\label{eq:frame-D13-contribution}
\partial_{D_{13}}\bigl(
  \alpha \otimes \alpha \otimes \alpha \otimes
  \eta_{12} \wedge \eta_{23}
\bigr)
= 0.
\end{equation}
This vanishing is specific to the chosen basis element
$\eta_{12} \wedge \eta_{23}$; for a general $2$-form,
$D_{13}$ can contribute.

\medskip
\noindent\textbf{Assembling the differential.}
Summing the three contributions
\eqref{eq:frame-D12-contribution}--\eqref{eq:frame-D13-contribution}:
\begin{equation}\label{eq:frame-dres-deg2}
d_{\mathrm{res}}\bigl(\alpha(z_1) \otimes \alpha(z_2)
\otimes \alpha(z_3) \otimes \eta_{12} \wedge \eta_{23}\bigr)
= k \cdot \alpha(z_3) \otimes \eta_{23}
  - k \cdot \alpha(z_1) \otimes \eta_{13}.
\end{equation}

\subsubsection*{Verification: $d_{\mathrm{res}}^2 = 0$ at degree~$2$}

Now apply $d_{\mathrm{res}}$ a second time.  Each term in the
right-hand side of~\eqref{eq:frame-dres-deg2} is a degree-$1$
element, and $d_{\mathrm{res}}$ on degree~$1$ extracts $k$
by~\eqref{eq:frame-dres-deg1}:
\begin{equation}\label{eq:frame-dsquared-deg2}
d_{\mathrm{res}}^2 = k \cdot d_{\mathrm{res}}(\alpha(z_3)
\otimes \eta_{23}) - k \cdot d_{\mathrm{res}}(\alpha(z_1)
\otimes \eta_{13}) = k^2 - k^2 = 0.
\end{equation}
The first term: $d_{\mathrm{res}}(\alpha(z_3) \otimes \eta_{23})$
extracts the OPE of $\alpha$ with itself at the collision
$z_2 = z_3$, giving $k$.  The second term:
$d_{\mathrm{res}}(\alpha(z_1) \otimes \eta_{13})$ extracts the
OPE at $z_1 = z_3$, also giving $k$.  These are equal, and
the relative sign~$-1$ forces exact cancellation.

\subsubsection*{Alternative basis and the role of $D_{13}$}

To see that the vanishing of $D_{13}$ above was a feature
of the basis choice, consider the alternative degree-$2$ element
$\alpha^{\otimes 3} \otimes \eta_{23} \wedge \eta_{31}$.
The Arnold relation~\eqref{eq:frame-arnold} below gives
\[
\eta_{23} \wedge \eta_{31}
= -\eta_{12} \wedge \eta_{23} - \eta_{31} \wedge \eta_{12}
= -\eta_{12} \wedge \eta_{23} + \eta_{12} \wedge \eta_{31}.
\]
Computing $d_{\mathrm{res}}$ on this element, the stratum $D_{13}$
\emph{does} contribute (with coefficient $+k$), but the stratum
$D_{12}$ picks up an additional sign.  The computation of
$d_{\mathrm{res}}^2 = 0$ on \emph{any} basis element
requires the \emph{full} Arnold relation, not just pairwise
cancellation.  The Arnold relation
is the universal identity guaranteeing $d^2 = 0$.

\begin{proposition}[Arnold relation; \ClaimStatusProvedHere]\label{prop:frame-arnold}
For any three distinct points $z_1, z_2, z_3 \in X$, the
logarithmic forms satisfy:
\begin{equation}\label{eq:frame-arnold}
\eta_{12} \wedge \eta_{23} + \eta_{23} \wedge \eta_{31}
+ \eta_{31} \wedge \eta_{12} = 0
\end{equation}
in $\Omega^2_{\log}(\overline{C}_3(X))$.
\end{proposition}

\begin{proof}
The identity $\frac{1}{z_1-z_2}\cdot\frac{1}{z_2-z_3}
+ \frac{1}{z_2-z_3}\cdot\frac{1}{z_3-z_1}
+ \frac{1}{z_3-z_1}\cdot\frac{1}{z_1-z_2} = 0$
follows from partial fractions: the three terms have
total numerator $(z_3-z_1)+(z_1-z_2)+(z_2-z_3) = 0$.
Taking $d\log$ of each factor and wedging produces
\eqref{eq:frame-arnold}.
\end{proof}

The Arnold relation forces $d^2 = 0$ on the bar complex.  At degree~$2$,
the two paths from $\bar{B}_2$ to $\bar{B}_0$ through $\bar{B}_1$
correspond to the two ``boundary of boundary'' strata in
$\overline{C}_3(X)$: $D_{12} \cap D_{23}$ and $D_{13} \cap D_{23}$.
The Arnold relation ensures these two paths contribute with opposite
signs, so they cancel.

More precisely: the differential $d$ on the bar complex is a sum of
residue maps along all collision divisors.  When $d$ is applied twice,
each pair of successive collisions defines a codimension-$2$ stratum
of $\overline{C}_{n+1}(X)$.  By Stokes' theorem on manifolds with
corners, $d^2 = 0$ if and only if the boundary of the boundary
vanishes, which is precisely the Arnold relation on the logarithmic
forms.

\begin{remark}[The Arnold relation as factorization coherence]
\label{rem:frame-arnold-factorization}
The identity~\eqref{eq:frame-arnold} is the fundamental coherence relation of factorization algebras: the bar complex is well-defined because Arnold holds, Verdier duality exchanges bar and cobar because Arnold is self-dual, and the genus tower extends over $\overline{\mathcal{M}}_g$ because Arnold lifts to boundary strata of the FM operad.  In the operadic language,~\eqref{eq:frame-arnold} defines the gravity operad $\mathrm{Grav} = \mathrm{HyCom}^!$, and the genus-$0$ bar-cobar adjunction is operadic Koszul duality.
\end{remark}

% ================================================================
\section{\texorpdfstring{The bar complex at all degrees --- $d^2 = 0$}{The bar complex at all degrees --- d squared equals zero}}
\label{sec:frame-bar-all}
% ================================================================

The pattern continues.  At degree~$n$, the bar complex element is
\begin{equation}\label{eq:frame-barn-element}
\alpha(z_1) \otimes \cdots \otimes \alpha(z_{n+1})
\otimes \eta_{i_1 j_1} \wedge \cdots \wedge \eta_{i_n j_n}
\end{equation}
and the bar differential extracts OPE data at each collision divisor.
Because the Heisenberg OPE has \emph{no simple pole}, the bracket
component $d_{\mathrm{bracket}}$ of the bar differential vanishes
identically.  Only the curvature component
$d_{\mathrm{curvature}}$ (which extracts the double-pole coefficient)
is nonzero.

Before stating the general theorem, we carry out the degree-$3$
computation in full detail.  This is the first degree where the
cancellation mechanism for $d^2 = 0$ involves \emph{pairs} of
Arnold relations, revealing the pattern that persists at all
higher degrees.

\subsection{\texorpdfstring{Explicit degree-$3$ computation ($n = 3$, four points)}{Explicit degree-3 computation (n = 3, four points)}}
\label{subsec:frame-degree3}

A degree-$3$ bar element lives on $\overline{C}_4(X)$ with four
points $z_1, z_2, z_3, z_4$ and involves a $3$-form in the
logarithmic algebra.  A natural basis element is:
\begin{equation}\label{eq:frame-bar3-element}
\xi_3 = \alpha(z_1) \otimes \alpha(z_2) \otimes \alpha(z_3)
  \otimes \alpha(z_4)
  \otimes \eta_{12} \wedge \eta_{23} \wedge \eta_{34}
  \;\in\; \bar{B}^{\mathrm{ch}}_3.
\end{equation}
This is the ``chain'' basis element, where the logarithmic forms
link consecutive pairs $1$--$2$, $2$--$3$, $3$--$4$.

\subsubsection*{Boundary strata of $\overline{C}_4(X)$}

The boundary divisors of $\overline{C}_4(X)$ are $D_{ij}$ for
$1 \leq i < j \leq 4$: there are $\binom{4}{2} = 6$ of them.
For each divisor $D_{ij}$, the bar differential extracts the
OPE $\alpha(z_i)\alpha(z_j) = k/(z_i - z_j)^2 + \mathrm{reg.}$,
collapses two of the four currents to the scalar $k$, and restricts
the $3$-form to a $2$-form on $\overline{C}_3(X)$.

We compute the contribution of each stratum.

\medskip
\noindent\textbf{Stratum $D_{12}$: collision $z_1 = z_2$.}
The form $\eta_{12}$ is consumed (it is the leftmost factor and
is the test form for $D_{12}$).  The OPE gives $k$.  The residual
$2$-form is $(\eta_{23} \wedge \eta_{34})|_{z_1 = z_2}$.  Since
$\eta_{23}$ and $\eta_{34}$ do not involve $z_1$ in a way that
changes under $z_1 = z_2$, the residual form is
$\eta_{23} \wedge \eta_{34}$ (with $z_1$ replaced by the
collision point $z_{12}$, but the forms only involve $z_2, z_3, z_4$).
The surviving currents are $\alpha(z_3)$ and $\alpha(z_4)$
(plus the collision point, which carries the scalar~$k$).
The sign is $+1$ (leftmost form consumed):
\begin{equation}\label{eq:frame-D12-deg3}
\partial_{D_{12}}(\xi_3)
= +k \cdot \alpha(z_3) \otimes \alpha(z_4)
  \otimes \eta_{23} \wedge \eta_{34}.
\end{equation}
(Here and below, we relabel the collision point: $z_{12}$ is
identified with $z_2$ on the residual configuration space.)

\medskip
\noindent\textbf{Stratum $D_{23}$: collision $z_2 = z_3$.}
The form $\eta_{23}$ must be consumed.  It sits in the middle
of the wedge product $\eta_{12} \wedge \eta_{23} \wedge \eta_{34}$.
Moving $\eta_{23}$ to the left past $\eta_{12}$ costs one
transposition sign:
\[
\eta_{12} \wedge \eta_{23} \wedge \eta_{34}
= -\eta_{23} \wedge \eta_{12} \wedge \eta_{34}.
\]
After consuming $\eta_{23}$, the residual $2$-form is
$\eta_{12}|_{z_2 = z_3} \wedge \eta_{34}|_{z_2 = z_3}
= \eta_{13} \wedge \eta_{34}$
(since $z_2 = z_3$ sends $\eta_{12} \mapsto \eta_{13}$
and leaves $\eta_{34}$ unchanged).
The surviving currents are $\alpha(z_1)$ and $\alpha(z_4)$:
\begin{equation}\label{eq:frame-D23-deg3}
\partial_{D_{23}}(\xi_3)
= -k \cdot \alpha(z_1) \otimes \alpha(z_4)
  \otimes \eta_{13} \wedge \eta_{34}.
\end{equation}

\medskip
\noindent\textbf{Stratum $D_{34}$: collision $z_3 = z_4$.}
The form $\eta_{34}$ is consumed.  It is the rightmost factor,
so moving it to the front costs two transpositions:
\[
\eta_{12} \wedge \eta_{23} \wedge \eta_{34}
= +\eta_{34} \wedge \eta_{12} \wedge \eta_{23}
\]
(two transpositions: $(-1)^2 = +1$; alternatively, a cyclic
permutation of three $1$-forms has sign $(-1)^{3-1} = +1$).
After consuming $\eta_{34}$, the residual $2$-form is
$\eta_{12} \wedge \eta_{23}|_{z_3 = z_4}
= \eta_{12} \wedge \eta_{23}$
(since $z_3 = z_4$ does not affect $\eta_{12}$ or $\eta_{23}$,
and we relabel the collision point as $z_3$).
The surviving currents are $\alpha(z_1)$ and $\alpha(z_2)$:
\begin{equation}\label{eq:frame-D34-deg3}
\partial_{D_{34}}(\xi_3)
= +k \cdot \alpha(z_1) \otimes \alpha(z_2)
  \otimes \eta_{12} \wedge \eta_{23}.
\end{equation}

\medskip
\noindent\textbf{Stratum $D_{13}$: collision $z_1 = z_3$.}
The form $\eta_{13}$ does not appear explicitly in the wedge
$\eta_{12} \wedge \eta_{23} \wedge \eta_{34}$.  We must restrict
each factor to $D_{13}$:
\begin{align*}
\eta_{12}\big|_{z_1 = z_3} &= \eta_{32} = -\eta_{23}, \\
\eta_{23}\big|_{z_1 = z_3} &= \eta_{23}, \\
\eta_{34}\big|_{z_1 = z_3} &= \eta_{34}.
\end{align*}
The restricted $3$-form is
$(-\eta_{23}) \wedge \eta_{23} \wedge \eta_{34}
= 0$
since $\eta_{23} \wedge \eta_{23} = 0$.
Therefore:
\begin{equation}\label{eq:frame-D13-deg3}
\partial_{D_{13}}(\xi_3) = 0.
\end{equation}

\medskip
\noindent\textbf{Stratum $D_{24}$: collision $z_2 = z_4$.}
Restrict each factor to $D_{24}$:
\begin{align*}
\eta_{12}\big|_{z_2 = z_4} &= \eta_{14}, \\
\eta_{23}\big|_{z_2 = z_4} &= \eta_{43} = -\eta_{34}, \\
\eta_{34}\big|_{z_2 = z_4} &= \eta_{34}.
\end{align*}
The restricted $3$-form is
$\eta_{14} \wedge (-\eta_{34}) \wedge \eta_{34}
= -\eta_{14} \wedge \eta_{34} \wedge \eta_{34} = 0$
since $\eta_{34} \wedge \eta_{34} = 0$.
Therefore:
\begin{equation}\label{eq:frame-D24-deg3}
\partial_{D_{24}}(\xi_3) = 0.
\end{equation}

\medskip
\noindent\textbf{Stratum $D_{14}$: collision $z_1 = z_4$.}
Restrict each factor to $D_{14}$:
\begin{align*}
\eta_{12}\big|_{z_1 = z_4} &= \eta_{42} = -\eta_{24}, \\
\eta_{23}\big|_{z_1 = z_4} &= \eta_{23}, \\
\eta_{34}\big|_{z_1 = z_4} &= \eta_{34}.
\end{align*}
After the collision $z_1 = z_4$, the restricted form
$(-\eta_{24}) \wedge \eta_{23} \wedge \eta_{34}$ is a $3$-fold wedge of
logarithmic $1$-forms on $\overline{C}_3(X)$ with coordinates
$(z_2, z_3, z_4)$.  By Arnold's theorem, the space of log-$1$-forms
on three points is $2$-dimensional (spanned by any two of
$\eta_{23}, \eta_{34}, \eta_{24}$, with the third determined by the
Arnold relation), so every $3$-fold wedge vanishes.
The boundary pairing therefore gives zero.
\begin{equation}\label{eq:frame-D14-deg3}
\partial_{D_{14}}(\xi_3) = 0.
\end{equation}

\subsubsection*{Assembling $d_{\mathrm{res}}$ at degree $3$}

Only the three ``adjacent'' strata $D_{12}$, $D_{23}$, $D_{34}$
contribute.  The three ``non-adjacent'' strata $D_{13}$, $D_{24}$,
$D_{14}$ all vanish by form-degree reasons.
Summing~\eqref{eq:frame-D12-deg3}--\eqref{eq:frame-D34-deg3}:
\begin{equation}\label{eq:frame-dres-deg3-full}
\boxed{\begin{aligned}
d_{\mathrm{res}}(\xi_3)
={} & k \cdot \alpha(z_3) \otimes \alpha(z_4)
    \otimes \eta_{23} \wedge \eta_{34} \\
  & {} - k \cdot \alpha(z_1) \otimes \alpha(z_4)
    \otimes \eta_{13} \wedge \eta_{34} \\
  & {} + k \cdot \alpha(z_1) \otimes \alpha(z_2)
    \otimes \eta_{12} \wedge \eta_{23}.
\end{aligned}}
\end{equation}
Observe the alternating signs $+, -, +$ from the position of the
consumed form in the wedge product: leftmost ($+1$), middle
($-1$), rightmost ($+1$).

\subsubsection*{Verification: $d_{\mathrm{res}}^2 = 0$ at degree~$3$}

We now apply $d_{\mathrm{res}}$ again to each of the three terms
in~\eqref{eq:frame-dres-deg3-full}.
Each term is a degree-$2$ element, and from
\eqref{eq:frame-dres-deg2} we know how $d_{\mathrm{res}}$ acts
at degree~$2$.

\medskip
\noindent\textbf{First term}: $d_{\mathrm{res}}\bigl(
k \cdot \alpha(z_3) \otimes \alpha(z_4)
\otimes \eta_{23} \wedge \eta_{34}\bigr)$.

The element $k \cdot \alpha(z_3) \otimes \alpha(z_4)
\otimes \eta_{23} \wedge \eta_{34}$ is a degree-$2$ element
on $\overline{C}_3$ with coordinates $(z_2, z_3, z_4)$,
carrying the scalar coefficient $k$ from the previous
contraction.  The two surviving currents sit at $z_3$
and~$z_4$.

The next residue can therefore come only from the OPE of
$\alpha(z_3)$ with $\alpha(z_4)$, hence from the boundary stratum
$D_{34}$.  Extracting that residue consumes $\eta_{34}$, and moving
that factor past $\eta_{23}$ contributes the sign $-1$:
\begin{equation}\label{eq:frame-dsq-T1}
d_{\mathrm{res}}\bigl(
  k \cdot \alpha(z_3) \otimes \alpha(z_4)
  \otimes \eta_{23} \wedge \eta_{34}\bigr)
= k \cdot (-1) \cdot k \cdot \eta_{23}\big|_{z_3 = z_4}
= -k^2 \cdot \eta_{24}.
\end{equation}

After the collapse $z_3 = z_4$, no currents remain.
The output $-k^2 \cdot \eta_{24}$ is a scalar $1$-form on
$\overline{C}_2$, equivalently an element of
$\bar{B}_1^{\mathrm{ch}}$ with scalar coefficient.  For the
cancellation argument, only the coefficient and sign matter.

\subsubsection*{Verification of $d^2 = 0$ via Arnold pairs}

Rather than applying $d_{\mathrm{res}}$ term-by-term to all
three summands and tracking relabeling, we verify $d^2 = 0$
structurally.  The bar differential
$d = d_{\mathrm{res}}$ satisfies $d^2 = 0$ if and only if
every codimension-$2$ boundary stratum of $\overline{C}_4(X)$
contributes zero.  The codimension-$2$ strata are of two types:

\medskip
\noindent\textbf{Type I: nested collisions} $D_{ij} \cap D_{jk}$
(three points $z_i, z_j, z_k$ collide in sequence).
These contribute via the composition
$\partial_{D_{jk}} \circ \partial_{D_{ij}}$:
first $z_i$ collides with $z_j$, then the collision point
collides with $z_k$.  The reverse order
$\partial_{D_{ij}} \circ \partial_{D_{jk}}$ gives the same
codimension-$2$ stratum with opposite orientation.  By the
Arnold relation on the triple $(z_i, z_j, z_k)$, these two
contributions cancel.

For the four-point configuration, the nested triples are:
$(1,2,3)$, $(2,3,4)$, $(1,2,4)$, $(1,3,4)$.
Each produces one Arnold-relation cancellation.

\medskip
\noindent\textbf{Type II: disjoint collisions} $D_{ij} \cap D_{kl}$
where $\{i,j\} \cap \{k,l\} = \emptyset$.
For four points, the only such stratum is $D_{12} \cap D_{34}$
(simultaneous collision $z_1 = z_2$ and $z_3 = z_4$).  The two
orderings $\partial_{D_{34}} \circ \partial_{D_{12}}$ and
$\partial_{D_{12}} \circ \partial_{D_{34}}$ commute (they act
on disjoint pairs), and the sign from the form restriction
ensures they cancel.  Explicitly, for the form
$\eta_{12} \wedge \eta_{23} \wedge \eta_{34}$:
\begin{itemize}
\item $\partial_{D_{12}}$ then $\partial_{D_{34}}$:
  consume $\eta_{12}$ (sign $+1$), leaving
  $\eta_{23} \wedge \eta_{34}$; then consume $\eta_{34}$
  (sign $-1$ from moving past $\eta_{23}$).  Net: $(-1)$.
\item $\partial_{D_{34}}$ then $\partial_{D_{12}}$:
  consume $\eta_{34}$ (sign $+1$ by cyclic permutation),
  leaving $\eta_{12} \wedge \eta_{23}$; then consume
  $\eta_{12}$ (sign $+1$).  Net: $(+1)$.
\end{itemize}
The two orderings produce opposite signs:
\begin{equation}\label{eq:frame-disjoint-cancel}
\partial_{D_{34}} \circ \partial_{D_{12}}(\xi_3)
+ \partial_{D_{12}} \circ \partial_{D_{34}}(\xi_3)
= k^2 \cdot (-1 + 1) = 0.
\end{equation}

\medskip
Since every codimension-$2$ stratum contributes zero (Type~I
by Arnold, Type~II by sign cancellation), we conclude:
\begin{equation}\label{eq:frame-dsquared-deg3}
\boxed{d_{\mathrm{res}}^2(\xi_3) = 0.}
\end{equation}
(The same conclusion can be reached by explicit term-by-term
computation of $d_{\mathrm{res}}$ applied to each summand
in~\eqref{eq:frame-dres-deg3-full}, using Arnold relations to
expose the residue factors; the boundary-stratum argument above
is cleaner and generalizes immediately to arbitrary degree.)

\subsubsection*{The adjacency pattern}

The degree-$3$ computation reveals a structural feature.  For
the chain basis element
$\alpha^{\otimes 4} \otimes \eta_{12} \wedge \eta_{23} \wedge \eta_{34}$,
only ``adjacent'' strata (those $D_{ij}$ where $\eta_{ij}$ appears
as a factor in the wedge) give nonzero contributions to~$d$.
The non-adjacent strata $D_{13}$, $D_{24}$, $D_{14}$ all vanish
by form-squaring ($\eta \wedge \eta = 0$).  This adjacency
pattern persists at all degrees for the chain basis: the
differential on
$\alpha^{\otimes(n+1)} \otimes \eta_{12} \wedge \eta_{23}
\wedge \cdots \wedge \eta_{n,n+1}$
receives contributions only from $D_{12}, D_{23}, \ldots, D_{n,n+1}$,
producing an alternating sum of $n$ terms with signs
$+1, -1, +1, -1, \ldots\,$

For a general basis element (not the chain basis), all strata can
contribute, and $d^2 = 0$ requires the full Arnold relation.
The chain basis is special precisely because it diagonalizes the
``adjacency'' of the logarithmic forms.

\subsection{The general theorem}

\begin{theorem}[Heisenberg bar complex at genus~\texorpdfstring{$0$}{0}; \ClaimStatusProvedHere]
\label{thm:frame-heisenberg-bar}
For $\mathcal{H}_k$ on $\mathbb{P}^1$:
\begin{equation}\label{eq:frame-heisenberg-bar-cohomology}
H^n(\bar{B}^{\mathrm{ch}}_{\mathrm{geom}}(\mathcal{H}_k))
= \begin{cases}
\mathbb{C} & n = 0, \\
0 & n = 1, \\
\mathbb{C} \cdot c_k & n = 2, \\
0 & n > 2.
\end{cases}
\end{equation}
The class $c_k \in H^2$ arises from the triple-collision residue
and is the homological manifestation of the central extension.
The differential satisfies $d^2 = 0$ at all degrees by the
Arnold relation.
\end{theorem}

\begin{proof}
\emph{Degree~$0$.}
$\bar{B}^0 = \mathbb{C} \cdot 1$ (vacuum), $d = 0$.

\emph{Degree~$1$.}
The differential $d_{\mathrm{res}}\colon \bar{B}^1 \to \bar{B}^0$
sends $\alpha(z_1) \otimes \alpha(z_2) \otimes \eta_{12} \mapsto k \cdot 1$
(equation~\eqref{eq:frame-dres-deg1}).
On $\mathbb{P}^1$, where $H^1(X) = 0$, this map is surjective
and has trivial kernel, so $H^1 = 0$.

\emph{Degree~$2$.}
The three-current collision produces the central charge class.
When $\alpha(z_1), \alpha(z_2), \alpha(z_3)$ approach a
common point, the iterated OPE produces:
\begin{equation}\label{eq:frame-triple-residue}
\mathrm{Res}_{D_{123}}\bigl[\alpha(z_1)\alpha(z_2)\alpha(z_3)
\otimes \eta_{12} \wedge \eta_{23}\bigr]
= k \cdot [\text{central class}]
\end{equation}
The commutator $[\alpha(z), \alpha(w)] = k \cdot
\partial_w\delta(z-w)$ contributes a central term at
the triple collision.  This produces a nontrivial
class $c_k \in H^2$.

\emph{Degrees $\geq 3$.}
Vanish by dimension counting: the Heisenberg algebra is
generated by a single current of conformal weight~$1$, and the
bar complex cohomology is controlled by the Lie algebra cohomology
of the abelian Lie algebra $\mathfrak{h}$, which is concentrated
in degrees $\leq 2$ for a $1$-dimensional central extension.

\emph{$d^2 = 0$.}
At each degree, $d^2 = 0$ by the Arnold relation
(Proposition~\ref{prop:frame-arnold}) applied to the
logarithmic forms on $\overline{C}_{n+1}(X)$.
The degree-$2$ verification is~\eqref{eq:frame-dsquared-deg2};
the general case follows by the same argument on all codimension-$2$
strata of $\overline{C}_{n+1}(X)$.
\end{proof}

The explicit degree-$2$ and degree-$3$ bar differentials confirm the
pattern.  The degree-$2$ computation is~\eqref{eq:frame-dres-deg2}
with $d^2 = 0$ by~\eqref{eq:frame-dsquared-deg2}; the degree-$3$
computation is~\eqref{eq:frame-dres-deg3-full} with $d^2 = 0$
by~\eqref{eq:frame-dsquared-deg3}.
At degree~$3$, the cancellation mechanism for $d^2 = 0$
involves both nested Arnold relations (Type~I) and disjoint-collision
sign cancellations (Type~II), as detailed in
\S\ref{subsec:frame-degree3}.

% ================================================================
\section{The twisting morphism: the propagator as algebraic map}
\label{sec:frame-twisting-morphism}
% ================================================================

The bar complex $\bar{B}(\mathcal{H}_k)$ is not merely an
abstract coalgebra attached to $\mathcal{H}_k$.  It carries a
canonical map back to $\mathcal{H}_k$ --- the \emph{universal
twisting morphism}
\begin{equation}\label{eq:frame-twisting-morphism}
\tau\colon \bar{B}(\mathcal{H}_k) \longrightarrow \mathcal{H}_k,
\end{equation}
defined by projecting a bar element to its single-insertion
(cogenerator) component.  Concretely, for a bar element
$\phi_1 \otimes \cdots \otimes \phi_n \otimes \omega
\in \bar{B}^n(\mathcal{H}_k)$:
\begin{equation}\label{eq:frame-tau-formula}
\tau(\phi_1 \otimes \cdots \otimes \phi_n \otimes \omega)
= \begin{cases}
  \phi_1 & n = 1,\;\omega = 1, \\[2pt]
  0 & n \geq 2.
\end{cases}
\end{equation}
The twisting morphism has degree~$+1$
(bar desuspension shifts degree by~$-1$).

\begin{proposition}[Maurer--Cartan equation for Heisenberg;
\ClaimStatusProvedHere]
\label{prop:frame-twisting-MC}
The twisting morphism~$\tau$ satisfies
\begin{equation}\label{eq:frame-MC}
d\tau + \tau \star \tau = 0
\end{equation}
in the convolution dg~Lie algebra
$\operatorname{Hom}(\bar{B}(\mathcal{H}_k), \mathcal{H}_k)$,
where $(\tau \star \tau)(x)
= \mu \circ (\tau \otimes \tau) \circ \Delta(x)$.
\end{proposition}

The geometric content of the Maurer--Cartan equation is that
it \emph{is the Arnold relation in algebraic disguise}.
The convolution $\tau \star \tau$ computes the residue of the
propagator $\eta_{12} = d\log(z_1 - z_2)$ at the collision
divisor $D_{12} \subset \overline{C}_2(\mathbb{P}^1)$.
The bar differential $d$ computes the boundary of this
residue.  The equation $d\tau + \tau \star \tau = 0$ says:
\emph{the boundary of a single collision cancels the
propagator residue} --- which is precisely Stokes' theorem
on $\overline{C}_2(\mathbb{P}^1)$.  At three points, this
becomes the Arnold relation.  At~$n$ points,
$d_{\mathrm{bar}}^2 = 0$.

\begin{proof}
\emph{Degree~$1$.}
For $x = \alpha^* \in \bar{B}^1$:
$\Delta(\alpha^*) = \alpha^* \otimes 1
+ 1 \otimes \alpha^*$ (primitive), so
$(\tau \star \tau)(\alpha^*) = 0$ (since $\tau(1) = 0$).
Also $d\tau(\alpha^*) = d(\alpha) = 0$.

\emph{Degree~$2$.}
For $x = \alpha^*(z_1) \otimes \alpha^*(z_2) \otimes \eta_{12}
\in \bar{B}^2$: the coproduct splits the pair, giving
$(\tau \star \tau)(x)
= \operatorname{Res}_{z_1 = z_2}
  [\alpha(z_1)\,\alpha(z_2)\,\eta_{12}]
= k$
(the OPE residue).
The bar differential gives
$d\tau(x) = \tau(d_{\mathrm{bar}}\,x) = -k$ by
equation~\eqref{eq:frame-dres-deg1}.
Hence $d\tau + \tau \star \tau = -k + k = 0$.
\end{proof}

\begin{definition}[Koszul complex for Heisenberg]
\label{def:frame-koszul-complex}
\index{Koszul complex!Heisenberg}
The \emph{Koszul complex} (twisted tensor product) of~$\tau$ is
\begin{equation}\label{eq:frame-koszul-complex}
K(\tau) := \mathcal{H}_k \otimes_\tau \bar{B}(\mathcal{H}_k)
= \bigl(\mathcal{H}_k \otimes \bar{B}(\mathcal{H}_k),\;
  d_{\mathcal{H}} + d_{\bar{B}} + d_\tau\bigr),
\end{equation}
where $d_\tau(\phi \otimes x) = \mu(\phi \otimes \tau(x_{(1)}))
\otimes x_{(2)}$ inserts $\tau$ of the first coproduct factor
into the algebra.
\end{definition}

By the fundamental theorem of twisting morphisms
(Theorem~\ref{thm:fundamental-twisting-morphisms}):
$\mathcal{H}_k$ is Koszul if and only if $K(\tau)$ is acyclic.
The bar cohomology of
Theorem~\ref{thm:frame-heisenberg-bar} (concentrated in
degrees~$0$ and~$2$) is exactly the obstruction to acyclicity
of $K(\tau)$; the unique class in degree~$2$ is the central
extension, and it is the twisting morphism that detects it.

The twisting morphism~$\tau$ determines everything computed in
this chapter: bar differential, Koszul complex, bar cohomology,
and Koszul dual (Corollary~\ref{cor:three-bijections}).
In the next section, the three bijections for $\tau$ become the
distinction between the Koszul dual \emph{coalgebra}, the Koszul
dual \emph{algebra}, and the bar-cobar \emph{resolution}.

\begin{remark}[The twisting morphism at higher genus]
\label{rem:frame-twisting-higher-genus}
At genus~$0$, the MC equation $d\tau + \tau\star\tau = 0$ holds
exactly: the propagator $\eta_{12} = d\log(z_1 - z_2)$ on
$\mathbb{P}^1$ is single-valued and the Arnold relation is exact.
At genus~$g \geq 1$, the propagator acquires monodromy and the
Arnold relation develops a defect
(Theorem~\ref{thm:quantum-arnold-relations}):
\[
d\tau_g + \tau_g \star \tau_g = \kappa(\mathcal{H}_k) \cdot \omega_g.
\]
The twisting morphism becomes \emph{curved}: the curvature
$\kappa \cdot \omega_g$ is the Arakelov form weighted by the level.
The corrected differential $\Dg{g}$ restores flatness by passing
to the holomorphic propagator
(Theorem~\ref{thm:quantum-diff-squares-zero};
Remark~\ref{rem:curved-twisting-higher-genus}).
\end{remark}

% ================================================================
\section{Reading off the Koszul dual}\label{sec:frame-koszul-dual}
% ================================================================

The bar coalgebra $\bar{B}(\mathcal{H}_k)$ carries a coproduct
determined by the OPE.  On the single cogenerator
$\alpha^* \in \bar{B}^1$, there is nothing to decompose:
\begin{equation}\label{eq:frame-primitive}
\Delta(\alpha^*) = \alpha^* \otimes 1 + 1 \otimes \alpha^*.
\end{equation}
This is the definition of a \emph{primitive} element.
Every element of $\bar{B}^1$ is primitive, and the
double-pole residue is symmetric under $z_i \leftrightarrow z_j$,
so the coproduct is cocommutative at all degrees.
The bar coalgebra is also conilpotent
(Theorem~\ref{thm:bar-nilpotency-complete}): every element
is eventually annihilated by iterated reduced coproducts.
By the Milnor--Moore theorem
(characteristic zero, conilpotent, cocommutative), such a
coalgebra is the universal enveloping coalgebra of its
primitives.  For $\mathcal{H}_k$ the space of primitives is
one-dimensional, so:
\begin{equation}\label{eq:frame-bar-coalgebra}
\bar{B}^{\mathrm{ch}}(\mathcal{H}_k)
\simeq \mathrm{coLie}^{\mathrm{ch}}(V^*),
\qquad V^* = \mathrm{Span}\{\alpha^*\}.
\end{equation}

\medskip
\noindent\textbf{Two constructions, two targets.}
From the coalgebra $\bar{B}(\mathcal{H}_k)$, two different
operations produce two different algebras:
\begin{enumerate}
\item \emph{Dualize} (graded linear dual):
$\mathrm{coLie}^{\mathrm{ch}}(V^*)^\vee
\cong \mathrm{Sym}^{\mathrm{ch}}(V^*)$,
the free commutative algebra in one generator ---
the \emph{Koszul dual algebra} $\mathcal{H}_k^!$.
\item \emph{Cobar} (free algebra on the desuspended coalgebra):
$\Omega(\bar{B}(\mathcal{H}_k))
\xrightarrow{\sim} \mathcal{H}_k$,
a quasi-isomorphism recovering the \emph{original} algebra
(Theorem~\ref{thm:bar-cobar-inversion-qi}).
\end{enumerate}
In display:
\begin{equation}\label{eq:frame-koszul-dual-coalgebra-to-algebra}
\bar{B}^{\mathrm{ch}}(\mathcal{H}_k)^\vee
\;\cong\; \mathrm{Sym}^{\mathrm{ch}}(V^*)
= \mathcal{H}_k^!
\end{equation}
versus
\[
\Omega\bigl(\bar{B}^{\mathrm{ch}}(\mathcal{H}_k)\bigr)
= \Omega\bigl(\mathrm{coLie}^{\mathrm{ch}}(V^*)\bigr)
\xrightarrow{\;\sim\;} \mathcal{H}_k.
\]
Dualizing changes the category (coalgebra $\to$ algebra,
coLie $\to$ Sym); cobar stays in the algebra category and
produces a resolution.  Both originate from
$\bar{B}(\mathcal{H}_k)$, but they point in opposite
algebraic directions --- and this is the $\mathrm{Com}^!
= \mathrm{Lie}$ duality made concrete.

The level $k$ determines a curvature element
$m_0 = -k \cdot \omega \in \mathrm{Sym}^2(V^*)$, encoding the
central extension.

\begin{theorem}[Heisenberg Koszul dual; \ClaimStatusProvedHere]
\label{thm:frame-heisenberg-koszul-dual}
The Koszul dual of $\mathcal{H}_k$ is the curved commutative
chiral algebra
\begin{equation}\label{eq:frame-koszul-dual}
\mathcal{H}_k^! \simeq \bigl(\mathrm{Sym}^{\mathrm{ch}}(V^*),\;
d = 0,\; m_0 = -k \cdot \omega\bigr).
\end{equation}
This is \emph{not} $\mathcal{H}_{-k}$: the Heisenberg algebra is
not self-dual.
\end{theorem}

The two algebras differ in every structural property:
\begin{center}
\small
\begin{tabular}{c|c}
\textbf{Heisenberg} $\mathcal{H}_k$ &
\textbf{Koszul dual} $\mathrm{Sym}^{\mathrm{ch}}(V^*)$ \\
\hline
Non-commutative & Commutative \\
$[\alpha, \alpha] = k \neq 0$ &
$\alpha \cdot \alpha = \alpha^2$ (commutes) \\
Central extension & No central extension \\
Double-pole OPE & Regular OPE \\
Lie-type & Com-type
\end{tabular}
\end{center}

For a general augmented chiral algebra~$\cA$, the same
two-arrow pattern holds: the bar $\bar{B}(\cA)$ is a coalgebra
(the Koszul dual \emph{coalgebra}), its linear dual
$\bar{B}(\cA)^\vee = \cA^!$ is the Koszul dual \emph{algebra}
(realized via Verdier duality on $\operatorname{Ran}(X)$;
Theorem~\ref{thm:bar-cobar-verdier}), and the cobar recovers
the original: $\Omega(\bar{B}(\cA)) \simeq \cA$ on the Koszul
locus (Theorem~\ref{thm:bar-cobar-inversion-qi}).  The general
bar-cobar adjunction is developed in
Chapter~\ref{chap:bar-cobar}.

\begin{remark}[The canonical twisting morphism for Heisenberg]
\label{rem:frame-twisting-morphism}
\index{twisting morphism!Heisenberg example}
The Koszul duality above is witnessed by the twisting morphism
$\tau_{\mathcal{H}} \colon \mathrm{coLie}^{\mathrm{ch}}(V^*)
\to \mathcal{H}_k$,
$v^* \mapsto J_v$.
It solves $\partial\tau + \tau \star \tau = 0$
because the only OPE pole is the double pole:
$\tau \star \tau$ extracts the level $k\omega(v,w)$,
which lies in the center and is killed by the augmentation.
The counit $\varepsilon_\tau$ is bar-cobar inversion
(\S\ref{sec:frame-inversion}); the unit $\eta_\tau$ is
bar concentration (Theorem~\ref{thm:frame-heisenberg-bar}).
\end{remark}

\begin{remark}[Three different ``dualities'']
\label{rem:frame-three-dualities}
Three distinct operations must not be confused: (1)~Koszul duality $\mathcal{H}_k \leftrightarrow \mathrm{Sym}^{\mathrm{ch}}(V^*)$, where the bar coalgebra $\bar{B}(\mathcal{H}_k)$ \emph{is} the Koszul dual coalgebra and its linear dual is the Koszul dual algebra~$\mathcal{H}_k^!$ (this chapter); (2)~level-shifting $\mathrm{Rep}(\mathcal{H}_k) \simeq \mathrm{Rep}(\mathcal{H}_{-k})$; (3)~boson-fermion correspondence $\mathrm{Rep}(\mathcal{H}_k) \simeq \mathrm{Rep}(\mathcal{F}^{\otimes 2})$.  Only~(1) is the subject of this monograph.
\end{remark}

% ================================================================
\section{Bar-cobar inversion --- Theorem B in action}
\label{sec:frame-inversion}
% ================================================================

The bar construction and the cobar construction form an adjoint
pair $\Omega \dashv \barB$ between augmented chiral algebras
and conilpotent chiral coalgebras
(Chapter~\ref{chap:bar-cobar}).  The counit of this adjunction
\begin{equation}\label{eq:frame-bar-cobar-inversion}
\varepsilon\colon
\Omega^{\mathrm{ch}}\bigl(\bar{B}^{\mathrm{ch}}(\mathcal{H}_k)\bigr)
\xrightarrow{\;\sim\;} \mathcal{H}_k
\end{equation}
is a quasi-isomorphism: the bar-cobar round trip recovers the
original algebra.

\subsection{The data flow}

The double-pole coefficient~$k$ passes through the bar-cobar
cycle without loss:
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}lll@{}}
\textbf{Stage} & \textbf{Data} & \textbf{Form} \\
\hline
$\mathcal{H}_k$ &
  $\alpha(z)\alpha(w) \sim k/(z{-}w)^2$ &
  OPE \\
$\barB$ &
  $d_{\mathrm{res}}(\alpha{\otimes}\alpha{\otimes}\eta_{12})
  = k$ &
  Residue \\
$H^*(\barB)$ &
  $c_k \in H^2\bigl(\barB(\mathcal{H}_k)\bigr)$ &
  Central class \\
$\Omega$ &
  $m_0 = -k\omega$ in $\Omega\barB(\mathcal{H}_k)$ &
  Curvature \\
$\varepsilon$ &
  $s\alpha^* \mapsto \alpha$ &
  OPE recovered
\end{tabular}
\end{center}
\noindent
The bar differential extracts~$k$ as a residue
(\S\ref{sec:frame-bar-deg1}); the bar cohomology stores it
in the central class~$c_k$
(Theorem~\ref{thm:frame-heisenberg-bar}); the cobar functor
reads the coalgebra structure of~$\barB(\mathcal{H}_k)$
and installs it as the differential of a free chiral
algebra on the cogenerator~$s\alpha^*$; the counit projects
to~$\mathcal{H}_k$.  Bar is a lossless encoding.

\subsection{The Koszul property}

$\mathcal{H}_k$ is Koszul: the bar cohomology
\[
H^n\bigl(\barB(\mathcal{H}_k)\bigr) =
\begin{cases}
\mathbb{C} & n = 0, \\
\mathbb{C} \cdot c_k & n = 2, \\
0 & \text{otherwise}
\end{cases}
\]
is concentrated in the minimal degrees consistent with the
central extension, so the bar complex is formal
(quasi-isomorphic to its cohomology as a coalgebra).
Formality forces the counit~$\varepsilon$ to be
a quasi-isomorphism: the resolution carries no higher
obstructions.

The chain of identifications underlying the duality:
\[
\bar{B}^{\mathrm{ch}}(\mathcal{H}_k)
\simeq \mathrm{coLie}^{\mathrm{ch}}(V^*)
\;\xrightarrow{\;\Omega\;}\;
\mathrm{Sym}^{\mathrm{ch}}(V^*)
= \mathcal{H}_k^!,
\qquad
\bar{B}^{\mathrm{ch}}(\mathcal{H}_k^!)
\simeq \mathrm{coLie}^{\mathrm{ch}}(V)
\;\xrightarrow{\;\Omega\;}\;
\mathcal{H}_k.
\]
The last step uses that the free Lie algebra on a single
generator is abelian ($\mathrm{Lie}(V) \cong V$ for
$\dim V = 1$).  The bar-cobar adjunction restricts to an
equivalence on the Koszul locus
(Theorem~\ref{thm:bar-cobar-isomorphism-main}):
$\mathcal{H}_k$ and $\mathcal{H}_k^!$ mutually determine
each other.

This is Theorem~B
(Theorem~\ref{thm:higher-genus-inversion})
for the simplest non-trivial case.  The general theorem
(with the $\mathrm{A}_0/\mathrm{A}_1/\mathrm{A}_2$ decomposition
of Remark~\ref{rem:theorem-A-decomposition}) establishes
bar-cobar duality for all augmented chiral algebras, with the
quasi-isomorphism $\Omega\barB(\cA) \xrightarrow{\sim}
\cA$ holding on the Koszul locus.  The PBW spectral sequence
(Chapter~\ref{chap:bar-cobar}) controls convergence:
affine Kac--Moody algebras and $\mathcal{W}$-algebras with
collapsing PBW sequence are all Koszul.

% ================================================================
\section{The passage to genus~1 --- curvature appears}
\label{sec:frame-genus1}
% ================================================================

Everything computed so far takes place on $\mathbb{P}^1$
(genus~$0$).  Replace $X = \mathbb{P}^1$ by an elliptic curve
$E_\tau = \mathbb{C}/(\mathbb{Z} + \tau\mathbb{Z})$ with modular
parameter $\tau \in \mathbb{H}$.

The propagator changes.  On $\mathbb{P}^1$, the logarithmic form
$\eta_{12} = d\log(z_1 - z_2)$ has a simple pole at $z_1 = z_2$
and is single-valued.  On $E_\tau$, no meromorphic function with
a single simple pole can be doubly periodic (Liouville's theorem).
The correct replacement is the \emph{elliptic propagator}:
\begin{equation}\label{eq:frame-elliptic-propagator}
G_\tau(z) = \zeta_\tau(z) + \frac{\pi^2 E_2(\tau)}{3}\, z
\end{equation}
where $\zeta_\tau(z)$ is the Weierstrass zeta function
\begin{equation}\label{eq:frame-weierstrass-zeta}
\zeta_\tau(z) = \frac{1}{z}
+ \sum_{(m,n) \neq (0,0)}\left[
  \frac{1}{z - m - n\tau}
  + \frac{1}{m + n\tau}
  + \frac{z}{(m+n\tau)^2}
\right]
\end{equation}
and $E_2(\tau)$ is the weight-$2$ Eisenstein series
\begin{equation}\label{eq:frame-E2}
E_2(\tau) = 1 - 24\sum_{n=1}^{\infty} \sigma_1(n)\, q^n,
\qquad q = e^{2\pi i \tau}.
\end{equation}

The Weierstrass $\zeta$-function is \emph{quasi-periodic}: it
satisfies $\zeta_\tau(z + 1) = \zeta_\tau(z) + 2\eta_1$ and
$\zeta_\tau(z + \tau) = \zeta_\tau(z) + 2\eta_2$, where the
quasi-periods are $\eta_1 = \pi^2 E_2(\tau)/6$.  The
$E_2$-correction in~\eqref{eq:frame-elliptic-propagator}
is the price of modular covariance: without it, the propagator
does not transform correctly under $\mathrm{SL}_2(\mathbb{Z})$.

The Laurent expansion near $z = 0$ is:
\begin{equation}\label{eq:frame-green-laurent}
G_\tau(z) = \frac{1}{z}
+ \frac{\pi^2 E_2(\tau)}{3}\, z + O(z^3).
\end{equation}
At genus~$0$, only the pole $1/z$ survives.  The $E_2$-term
is the first appearance of modular forms in the bar complex.

\subsection{The genus-1 two-point function}

The Heisenberg two-point function on $E_\tau$ is
\begin{equation}\label{eq:frame-genus1-2pt}
\langle \alpha(z_1)\, \alpha(z_2) \rangle_{E_\tau}
= k \cdot G_\tau(z_1 - z_2).
\end{equation}

The genus-$1$ partition function is computed by the following theorem.

\begin{theorem}[Genus-1 Heisenberg partition function; \ClaimStatusProvedHere]\label{thm:genus1-heisenberg}
The genus-$1$ partition function of the Heisenberg algebra $\mathcal{H}_k$ on the elliptic curve $E_\tau$ is
\begin{equation}\label{eq:frame-partition-g1}
Z_{E_\tau}^{\mathcal{H}} =
\mathrm{Tr}_{\mathcal{F}_k}\, q^{L_0 - c/24}
= \frac{1}{\eta(\tau)}
= q^{-1/24}\prod_{n=1}^{\infty}\frac{1}{1-q^n}
\end{equation}
where $\eta(\tau)$ is the Dedekind eta function.  The coefficients
are the partition numbers $p(n)$: the number of partitions of $n$
counts the number of states at excitation level~$n$ in the
Fock space.
\end{theorem}

\subsection{\texorpdfstring{Curvature: $\dfib^{\,2} \neq 0$ at genus 1}{Curvature: d fib squared is not zero at genus 1}}

Compute the bar differential on $E_\tau$ using the elliptic
propagator~\eqref{eq:frame-elliptic-propagator}.  The B-cycle
monodromy of $G_\tau$ produces a defect: transporting the
propagator around the B-cycle of $E_\tau$ shifts it by the
constant $-2\pi i$.  This shift is the genus-$1$ curvature.

\begin{theorem}[Genus-1 curvature; \ClaimStatusProvedHere]\label{thm:frame-genus1-curvature}
For $\mathcal{H}_k$ on $E_\tau$, the fiberwise differential satisfies
\begin{equation}\label{eq:frame-dsquared-genus1}
\dfib^{\,2} = k \cdot \omega_1 \cdot \mathrm{id}
\end{equation}
where $\omega_1 = c_1(\mathbb{E}) \in H^2(\overline{\mathcal{M}}_1)$
is the first Chern class of the Hodge bundle on the moduli space
of elliptic curves.
\end{theorem}

The proof is the direct computation: the B-cycle monodromy of the
elliptic propagator contributes a phase $e^{2\pi i k}$ to the
parallel transport of bar complex elements.  Squaring the
differential, the two B-cycle transports contribute a factor
$(-2\pi i)^2$ that, after integration over $\overline{\mathcal{M}}_1$,
produces the Hodge class $\omega_1 = c_1(\mathbb{E})$ with
coefficient~$k$.  The detailed computation appears in
Theorem~\ref{thm:heisenberg-obs}.

The fiberwise differential has ceased to be strictly square-zero.

At genus~$0$, the bar complex was a genuine chain complex
($\dzero^{\,2} = 0$) and its cohomology was well-defined.  At genus~$1$,
the bar complex is \emph{curved}: $\dfib^{\,2} = k \cdot \omega_1$
is proportional to the level.  The curvature vanishes only at
$k = 0$, where the Heisenberg algebra degenerates.

\begin{remark}[Physical meaning of curvature]
\label{rem:frame-curvature-physics}
The curvature $\dfib^{\,2} = k \cdot \omega_1$ is the conformal anomaly: $k$ controls the central extension strength, $\omega_1$ is the gravitational coupling, and $k \cdot \omega_1 = c_1(\det(R\pi_*\mathcal{F}_k))$ on $\overline{\mathcal{M}}_1$ measures the obstruction to consistent definition on all elliptic curves.
\end{remark}

% ================================================================
\section{\texorpdfstring{The holomorphic anomaly and $E_2$}{The holomorphic anomaly and E2}}
\label{sec:frame-holomorphic-anomaly}
% ================================================================

The appearance of $E_2$ introduces a \emph{holomorphic anomaly}.
Under modular transformations $\tau \mapsto (a\tau+b)/(c\tau+d)$,
the weight-$4$ and weight-$6$ Eisenstein series transform as
modular forms:
\[
E_4(\gamma \cdot \tau) = (c\tau+d)^4 E_4(\tau), \qquad
E_6(\gamma \cdot \tau) = (c\tau+d)^6 E_6(\tau).
\]
The weight-$2$ Eisenstein series does not:
\begin{equation}\label{eq:frame-E2-anomaly}
E_2\!\left(\frac{a\tau+b}{c\tau+d}\right)
= (c\tau+d)^2 E_2(\tau) + \frac{6c(c\tau+d)}{\pi i}.
\end{equation}
The extra term $6c(c\tau+d)/(\pi i)$ is the holomorphic anomaly.

For the Heisenberg two-point function on $E_\tau$, this anomaly
produces:
\begin{equation}\label{eq:frame-2pt-anomaly}
\langle \alpha(z_1)\, \alpha(z_2) \rangle_{\gamma \cdot \tau}
= (c\tau+d)^2
  \langle \alpha((c\tau+d)^{-1}z_1)\,
  \alpha((c\tau+d)^{-1}z_2) \rangle_\tau
  - \frac{6ck}{\pi i}\, z_{12}.
\end{equation}
The anomaly term is proportional to $k$ (the level) and to $c$
(the lower-left entry of the modular matrix).

This is the genus-$1$ obstruction class
(Theorem~\ref{thm:frame-genus1-curvature}), seen from the modular
side.  The bar complex curvature $\dfib^{\,2} = k \cdot \omega_1$ and the
holomorphic anomaly in $E_2$ are two manifestations of the same
phenomenon: the failure of the Heisenberg algebra to extend
coherently over the moduli space $\overline{\mathcal{M}}_1$.

% ================================================================
\section{Why the ordinary derived category fails}
\label{sec:frame-coderived}
% ================================================================

The curvature $\dfib^{\,2} = k \cdot \omega_1$ means that the genus-$1$
bar complex is not a chain complex in the ordinary sense: it does
not live in the derived category $D(\mathrm{Vect})$.  It lives in
the \emph{coderived category} $D^{\mathrm{co}}(\mathrm{Vect})$ of
Positselski~\cite{Positselski11}.

In the ordinary derived
category, a complex with $\dfib^{\,2} \neq 0$ is simply undefined.  In
Positselski's framework, a \emph{curved} differential graded
(co)algebra --- one where $\dfib^{\,2} = m_0 \neq 0$ for some curvature
element $m_0$ --- has a well-defined coderived category in which:
\begin{enumerate}
\item The bar-cobar adjunction still holds (as an adjunction of
  curved (co)algebras).
\item The notion of ``acyclic'' is refined: a curved complex can
  be \emph{coacyclic} (contractible in the coderived sense) without
  being acyclic in the ordinary sense.
\item The bar-cobar quasi-isomorphism
  $\Omega(\bar{B}(\mathcal{A})) \to \mathcal{A}$ holds in the
  coderived category when it fails in the ordinary derived category.
\end{enumerate}

The Heisenberg algebra at $k \neq 0$ is the simplest object that
forces us out of the ordinary derived category.  At $k = 0$,
$\dfib^{\,2} = 0$ and the ordinary derived category suffices; at $k \neq 0$,
the curvature is nonzero and only the coderived category gives the
correct homological algebra.

The genus-$1$ bar complex of
$\mathcal{H}_k$ with $k \neq 0$ is ``acyclic'' in the na\"ive sense
(its homology with respect to $\dfib$ is zero, since $\dfib^{\,2} \neq 0$
means the notion of ``homology'' is undefined), but it is
\emph{not coacyclic} in Positselski's sense --- it carries
genuine invariants (the Hodge class $\omega_1$, the partition
function $1/\eta(\tau)$) that are invisible to ordinary
homological algebra but visible in the coderived category.

The general theory of bar-cobar duality in the coderived
setting is developed in
Chapter~\ref{chap:bar-cobar}
(Theorem~\ref{thm:bar-cobar-isomorphism-main}).

% ================================================================
\section{Genus~2 --- Siegel modular forms}\label{sec:frame-genus2}
% ================================================================

At genus~$2$, the Riemann surface $\Sigma_2$ has period matrix
$\Omega = \bigl(\begin{smallmatrix} \tau_1 & z \\ z & \tau_2
\end{smallmatrix}\bigr) \in \mathcal{H}_2$ (the Siegel upper
half-space).  The genus-$2$ propagator is
\begin{equation}\label{eq:frame-genus2-propagator}
K^{(2)}(w_1, w_2 \,|\, \Omega)
= \partial_{w_1} \log E(w_1, w_2;\, \Omega)
\end{equation}
where $E(w_1, w_2;\, \Omega)$ is the prime form on~$\Sigma_2$.

Near $w_1 = w_2$, the prime form has the expansion
\begin{equation}\label{eq:frame-prime-form-expansion}
E(w_1, w_2;\, \Omega)
= (w_1 - w_2)\bigl(1 + c_2(\Omega)(w_1 - w_2)^2
+ c_4(\Omega)(w_1 - w_2)^4 + \cdots\bigr)
\end{equation}
where the coefficients $c_{2j}(\Omega)$ are Siegel modular forms
for $\mathrm{Sp}(4, \mathbb{Z})$.

Three features invisible at genus~$1$ emerge:
\begin{enumerate}
\item \emph{Multi-dimensional Hodge bundle.}
  At genus~$1$, the Hodge bundle $\mathbb{E}$ is a line bundle and
  $\lambda_1 = c_1(\mathbb{E})$.  At genus~$2$, $\mathbb{E}$ has
  rank~$2$, and $\lambda_2 = c_2(\mathbb{E})$ is a determinantal
  class involving the interaction of both B-cycle monodromies.

\item \emph{Off-diagonal periods.}
  The entry $z = \Omega_{12}$ encodes the interaction between the
  two handles of $\Sigma_2$.

\item \emph{Function-valued monodromies.}
  The genus-$1$ B-cycle monodromy of the propagator is the
  constant~$-2\pi i$.  At genus~$2$, the monodromies
  $-2\pi i \cdot \omega_j(w)$ are sections of
  $\omega_{\Sigma_2}$.  Each B-cycle defect contributes a
  $2$-form on moduli space, and the two defects combine
  multiplicatively: hence $\lambda_2$ lives in $H^4$
  (not~$H^2$).
\end{enumerate}

\begin{theorem}[Genus-2 curvature; \ClaimStatusProvedHere]\label{thm:frame-genus2-curvature}
The genus-$2$ bar complex of $\mathcal{H}_k$ has curvature:
\begin{equation}\label{eq:frame-genus2-curvature}
(d^{(2)})^2 = k \cdot \lambda_2
\end{equation}
where $\lambda_2 = c_2(\mathbb{E}) \in H^4(\overline{\mathcal{M}}_2)$.
\end{theorem}

The free energy at genus~$2$ is
\begin{equation}\label{eq:frame-F2}
F_2(\mathcal{H}_k) = k \cdot
\int_{\overline{\mathcal{M}}_{2,1}} \psi_1^2\, \lambda_2
= k \cdot \frac{7}{8} \cdot \frac{|B_4|}{4!}
= \frac{7k}{5760}
\end{equation}
where $B_4 = -1/30$ is the fourth Bernoulli number.

% ================================================================
\section{\texorpdfstring{The genus tower --- recognizing the $\hat{A}$-genus}{The genus tower --- recognizing the A-hat genus}}
\label{sec:frame-genus-tower}
% ================================================================

The pattern from genus~$1$ and genus~$2$ extends.  At genus~$g$,
the bar complex curvature is
\begin{equation}\label{eq:frame-genus-g-curvature}
\dfib^{\,2} = k \cdot \lambda_g
\end{equation}
where $\lambda_g = c_g(\mathbb{E}) \in H^{2g}(\overline{\mathcal{M}}_g)$
is the top Chern class of the Hodge bundle
(Theorem~\ref{thm:heisenberg-obs}).
This genus tower is the simplest instance of the explicit universal
MC class (Theorem~\ref{thm:explicit-theta}):
$\Theta_{\mathcal{H}_k}^{\min} = k \cdot \eta \otimes \Lambda$,
where $\Lambda = \sum_{g \geq 1}\lambda_g$.
For Heisenberg, $\kappa = k$ and the spectral discriminant is trivial
($\Delta = 1$), so the full modular package reduces to this single
formula.  The $\hat{A}$-genus emerges because
$\operatorname{tr}(\Theta) = k \cdot (\hat{A}(ix) - 1)$
(Theorem~\ref{thm:family-index}): the Todd class of the universal
curve, pushed forward by GRR, \emph{is} the genus tower.

The genus-$g$ free energy is
\begin{equation}\label{eq:frame-Fg}
F_g(\mathcal{H}_k) = k \cdot
\frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}
\end{equation}
for all $g \geq 1$ (Theorem~\ref{thm:heisenberg-all-genera}).
The first values are:
\begin{align}
F_1 &= k \cdot \frac{1}{24}, \label{eq:frame-F1} \\
F_2 &= k \cdot \frac{7}{5760}, \label{eq:frame-F2-repeat} \\
F_3 &= k \cdot \frac{31}{967680}, \label{eq:frame-F3} \\
F_4 &= k \cdot \frac{127}{154828800}. \label{eq:frame-F4}
\end{align}

The generating function assembles these into a closed form:
\begin{equation}\label{eq:frame-generating-function}
\sum_{g=1}^{\infty} F_g(\mathcal{H}_k)\, x^{2g}
= k\left(\frac{x/2}{\sin(x/2)} - 1\right).
\end{equation}

Including the leading term ($g = 0$, where $F_0 = 1$ by convention):
\begin{equation}\label{eq:frame-full-generating}
1 + \sum_{g=1}^{\infty} F_g\, x^{2g}
= \frac{x/2}{\sin(x/2)}.
\end{equation}

The function $x/2 / \sin(x/2)$ is the $\hat{A}$-genus evaluated at
imaginary argument.  The $\hat{A}$-genus of a complex manifold~$M$
is the multiplicative genus associated to the power series
\begin{equation}\label{eq:frame-a-hat-def}
\hat{A}(x) = \frac{x/2}{\sinh(x/2)}
= 1 - \frac{x^2}{24} + \frac{7x^4}{5760} - \cdots
\end{equation}
and the Wick rotation $x \mapsto ix$ sends $\sinh(x/2)$ to
$i\sin(x/2)$, producing precisely the generating
function~\eqref{eq:frame-full-generating}.

This follows from the
Faber--Pandharipande $\lambda_g$ formula and the Grothendieck--Riemann--Roch
theorem.  We derive both connections here.

\subsubsection*{The Faber--Pandharipande formula}

The genus-$g$ obstruction class is
$\mathrm{obs}_g(\mathcal{H}_k) = k \cdot \lambda_g$
where $\lambda_g = c_g(\mathbb{E}) \in H^{2g}(\overline{\mathcal{M}}_g)$
is the top Chern class of the Hodge bundle
$\mathbb{E} = \pi_*\omega_{\mathcal{C}/\overline{\mathcal{M}}_g}$.
The free energy extracts this as a number via integration against
powers of the cotangent line class $\psi_1 = c_1(\mathbb{L}_1)$
on $\overline{\mathcal{M}}_{g,1}$:
\begin{equation}\label{eq:frame-fp-integral}
F_g(\mathcal{H}_k) = k \cdot
\int_{\overline{\mathcal{M}}_{g,1}} \psi_1^{2g-2}\, \lambda_g.
\end{equation}
The Faber--Pandharipande formula~\cite{FP00} evaluates this integral:
\begin{equation}\label{eq:frame-fp-formula}
\int_{\overline{\mathcal{M}}_{g,1}} \psi_1^{2g-2}\, \lambda_g
= \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}
\end{equation}
where $B_{2g}$ is the $2g$-th Bernoulli number.

The connection to the $\hat{A}$-genus is visible at the level of
generating functions.  The Bernoulli numbers are defined by
\begin{equation}\label{eq:frame-bernoulli-gf}
\frac{x}{e^x - 1} = \sum_{n=0}^{\infty} \frac{B_n}{n!}\, x^n
= 1 - \frac{x}{2} + \frac{x^2}{12} - \frac{x^4}{720} + \cdots
\end{equation}
which is the Todd genus generating function.  The factor
$(2^{2g-1}-1)/2^{2g-1}$ in~\eqref{eq:frame-fp-formula} arises
from the relationship between the Todd class and the $\hat{A}$-class:
\begin{equation}\label{eq:frame-todd-ahat}
\mathrm{Td}(x) = \frac{x}{1 - e^{-x}} = e^{x/2} \cdot \hat{A}(x),
\qquad
\hat{A}(x) = \frac{x/2}{\sinh(x/2)}.
\end{equation}
Expanding $\hat{A}(x) = \sum_{g=0}^{\infty} a_g\, x^{2g}$
(the $\hat{A}$-class is even), the coefficients are
\begin{equation}\label{eq:frame-ahat-bernoulli}
a_g = \frac{(-1)^g(2^{2g-1}-1)}{2^{2g-1}} \cdot \frac{B_{2g}}{(2g)!}
\end{equation}
which matches~\eqref{eq:frame-fp-formula} up to the sign
$(-1)^g$ absorbed by the Wick rotation $x \mapsto ix$.
This confirms equation~\eqref{eq:frame-full-generating}.

\subsubsection*{The GRR derivation}

\begin{remark}[The family index theorem]
\label{rem:frame-family-index}
The $\hat{A}$-genus arises from Grothendieck--Riemann--Roch (Theorem~\ref{thm:family-index}).  For $\mathcal{H}_k$, the modular deformation complex is $k \cdot \mathbb{E}$; the GRR formula
\begin{equation}\label{eq:frame-grr}
\mathrm{ch}(\pi_!\, \omega_{\mathcal{C}})
= \pi_*\!\left(\mathrm{ch}(\omega_{\mathcal{C}}) \cdot
\mathrm{Td}(T_\pi)\right)
\end{equation}
applied to $\pi\colon \overline{\mathcal{M}}_{g,1} \to \overline{\mathcal{M}}_g$ recovers the Mumford formula $\mathrm{ch}_g(\mathbb{E}) = B_{2g} \cdot \kappa_{2g-1}/(2g)!$, which combined with $\mathrm{obs}_g = k \cdot \lambda_g$ yields~\eqref{eq:frame-generating-function}.  The genus expansion of every Koszul chiral algebra is an index: the $\hat{A}$-class pushforward of the Hodge bundle scaled by bar-complex curvature.
\end{remark}

\begin{table}[ht]
\centering
\caption{Free energy values $F_g$ for $\mathcal{H}_k$ ($k = 1$),
genera $1 \leq g \leq 6$}
\label{tab:frame-free-energy}
\begin{tabular}{|c|c|c|c|}
\hline
$g$ & $F_g$ (exact) & $F_g$ (decimal) &
  Bernoulli $|B_{2g}|$ \\
\hline
1 & $1/24$ & $4.17 \times 10^{-2}$ & $1/6$ \\
2 & $7/5760$ & $1.22 \times 10^{-3}$ & $1/30$ \\
3 & $31/967680$ & $3.20 \times 10^{-5}$ & $1/42$ \\
4 & $127/154828800$ & $8.20 \times 10^{-7}$ & $1/30$ \\
5 & $511/24524881920$ & $2.08 \times 10^{-8}$ & $5/66$ \\
6 & $1414477/2678117105664000$ & $5.28 \times 10^{-10}$ &
$691/2730$ \\
\hline
\end{tabular}
\end{table}

The generating function~\eqref{eq:frame-generating-function} has
radius of convergence $|x| < 2\pi$ (the first zero of $\sin(x/2)$
is at $x = 2\pi$).  The free energies $F_g$ decrease factorially,
and the genus expansion is convergent --- unlike the
genus expansion of the physical partition function, which grows as
$(2g)!$ (Mirzakhani volumes) and is only asymptotic.

% ================================================================
\section{Complementarity --- Theorem C in action}
\label{sec:frame-complementarity}
% ================================================================

The Heisenberg algebra $\mathcal{H}_k$ and its Koszul dual
$\mathcal{H}_k^! = \mathrm{Sym}^{\mathrm{ch}}(V^*)$ form
a Koszul pair.  Their genus-$g$ quantum corrections are
complementary.

\begin{theorem}[Quantum complementarity for Heisenberg; \ClaimStatusProvedHere]
\label{thm:frame-complementarity}
For the Koszul pair
$(\mathcal{H}_k, \mathrm{Sym}^{\mathrm{ch}}(V^*))$
at genus~$g$:
\begin{equation}\label{eq:frame-complementarity}
Q_g(\mathcal{H}_k) + Q_g(\mathcal{H}_k^!)
= H^*(\overline{\mathcal{M}}_g,\, \mathcal{Z}(\mathcal{H}_k))
\end{equation}
where $Q_g$ denotes the genus-$g$ quantum correction (the
obstruction to extending the genus-$0$ bar-cobar
quasi-isomorphism to genus~$g$), and $\mathcal{Z}(\mathcal{H}_k)$
is the center local system on~$\overline{\mathcal{M}}_g$.
\end{theorem}

At genus~$1$:
\begin{itemize}
\item The Heisenberg deformation space is one-dimensional,
  generated by the level~$k$.
\item The obstruction space of $\mathrm{Sym}^{\mathrm{ch}}(V^*)$
  is also one-dimensional, generated by the curvature
  $m_0 = -k \cdot \omega$.
\item Together, they span $H^*(\overline{\mathcal{M}}_1,
  \mathcal{Z}(\mathcal{H}_k)) \cong \mathbb{C}^2$.
\end{itemize}

The complementarity is controlled by Verdier duality on
$\overline{\mathcal{M}}_g$: the bar complex computes
deformations, the cobar complex computes obstructions,
and Verdier duality exchanges them.  What $\mathcal{H}_k$ sees
as a deformation (varying the level~$k$), its Koszul dual
sees as an obstruction (the curvature $m_0$), and vice versa.

This is Theorem~C
(Theorem~\ref{thm:quantum-complementarity-main})
for the Heisenberg case.  The general theorem establishes
complementarity for all Koszul chiral algebra pairs, with the
ambient space $H^*(\overline{\mathcal{M}}_g, \mathcal{Z})$
carrying a shifted-symplectic pairing from Verdier duality on
the center local system.

% ================================================================
\section{The characteristic hierarchy in the Heisenberg frame}
\label{sec:frame-modular-package}
% ================================================================

Everything computed in this chapter --- the bar complex,
the Koszul dual, the curvature at each genus, the free energy
tower, the complementarity --- assembles into a characteristic
hierarchy with three proved layers: a scalar package, an
ambient/spectral shadow, and a full homotopy completion
(Theorem~\ref{thm:mc2-bar-intrinsic}).

\begin{definition}[Characteristic hierarchy for Heisenberg]
\label{def:frame-modular-package}
The Heisenberg frame exhibits the following characteristic data:
\begin{enumerate}
\item The \emph{proved scalar characteristic data}
  $\kappa(\mathcal{H}_k) = k$
  (Theorem~\ref{thm:modular-characteristic}), which determines
  the entire \emph{scalar} modular package: $\mathrm{obs}_g = k
  \cdot \lambda_g$ for all $g \geq 1$.

\item The \emph{proved ambient complementarity complex}
  \begin{equation}\label{eq:frame-ambient}
  H_{\mathcal{H}_k}
  \coloneqq R\Gamma\bigl(\overline{\mathcal{M}}_g,\,
  \mathcal{Z}_{\mathcal{H}_k}\bigr)
  \end{equation}
  Verdier duality then provides the shifted-symplectic
  structure needed for complementarity
  \textup{(}Theorem~\ref{thm:quantum-complementarity-main}\textup{)}.

\item The \emph{proved spectral shadow}
  $\Delta_{\mathcal{H}_k}(x) = 1$
  (trivial for rank~$1$; for affine Kac--Moody algebras, the
  discriminant acquires the form
  $\Delta(x) = (1-3x)(1+x)$;
  Theorem~\ref{thm:spectral-characteristic}).

\item The \emph{proved full homotopy completion}
  \begin{equation}\label{eq:frame-MC-class}
  \Theta_{\mathcal{H}_k} \in
  \mathrm{MC}\!\left(
    \mathrm{Def}_{\mathrm{cyc}}(\mathcal{H}_k)
    \;\widehat{\otimes}\;
    R\Gamma\!\left(\overline{\mathcal{M}}_{g,\bullet},\,
    \mathbb{Q}\right)
  \right)
  \end{equation}
  whose scalar trace recovers items~(1)--(3).
  The universal class $\Theta_{\mathcal{H}_k}$ is constructed
  by Theorem~\ref{thm:mc2-bar-intrinsic}; for Heisenberg
  the non-scalar content is trivial ($\Delta = 1$), so the
  full modular package reduces to the scalar hierarchy
  (Theorem~\ref{thm:universal-theta}).
\end{enumerate}
\end{definition}

For the Heisenberg algebra, the scalar genus tower is fully determined
by the single number $\kappa = k$, and the spectral shadow is trivial:
$\Delta_{\mathcal{H}_k}(x)=1$.  This collapse is an artifact of the
abelian (rank-$1$) structure.  In Chapters~\ref{chap:kac-moody-koszul}
and~\ref{chap:w-algebras}, the hierarchy acquires non-trivial spectral
discriminant and richer ambient deformation data.

\begin{remark}[Hierarchy and status]%
\label{rem:frame-kappa-not-fundamental}
Definition~\ref{def:frame-modular-package} is a hierarchy: items~(1)--(3) are proved (Theorems~\ref{thm:modular-characteristic}, \ref{thm:quantum-complementarity-main}, \ref{thm:spectral-characteristic}); item~(4), the shadow Postnikov tower $\Theta_{\mathcal{A}}^{\leq r}$ (Definition~\ref{def:shadow-postnikov-tower}), is proved at finite order through arity~$4$, with scalar saturation for one-channel families (Theorem~\ref{thm:universal-theta}); the all-arity limit exists by the bar-intrinsic construction (Theorem~\ref{thm:mc2-bar-intrinsic}).  The genus-$1$ coefficient $\kappa(\mathcal{A})$ ($= k$ for Heisenberg, $c/2$ for Virasoro, $(k+h^\vee)\dim(\mathfrak{g})/(2h^\vee)$ for KM) is the scalar level $\Theta_{\mathcal{A}}^{\leq 2}$ of the tower, not the fundamental object.
\end{remark}

% ================================================================
\section{Free fields and the Lie--Com duality}
\label{sec:frame-free-fields}
% ================================================================

The Heisenberg algebra has a single bosonic current with a
\emph{double} pole.  The free fermion has a single
\emph{fermionic} current with a \emph{simple} pole:
\begin{equation}\label{eq:frame-fermion-ope}
\psi(z)\,\psi(w) = \frac{1}{z-w} + \text{regular}.
\end{equation}
Two differences from Heisenberg: the pole order drops from~$2$
to~$1$, and the statistics change from bosonic to fermionic.
Each has an independent algebraic consequence.

The first difference concerns pole order: the simple pole means
that the bar differential $d = d_{\mathrm{bracket}}$ has no
curvature component and is entirely bracket-type.  At degree~$1$,
it extracts the simple-pole residue
$\operatorname{Res}_{z=w} \psi(z)\psi(w) = 1$, a scalar.

The second, and more consequential, difference concerns statistics.
The Koszul sign rule acts on the bar complex: since $\psi$ is
fermionic ($|\psi| = 1$), two desuspended cogenerators in
$\bar{B}^2$ satisfy
$\psi^* \otimes \psi^* = -\psi^* \otimes \psi^*$ under
transposition, forcing antisymmetry.  The coproduct on
$\bar{B}(\mathcal{F})$ is therefore co-antisymmetric, so the
bar coalgebra is a coLie coalgebra and the Koszul dual algebra is
the commutative algebra $\mathrm{Com}$.  This is the classical
duality $\mathrm{Lie}^! = \mathrm{Com}$, already visible in the
OPE: the self-pairing $\psi(z)\psi(w) \sim 1/(z-w)$ is
antisymmetric under $z \leftrightarrow w$ (fermionic), encoding
Lie structure.

By contrast, the Heisenberg current $\alpha$ is bosonic
($|\alpha| = 0$), so the desuspended cogenerators commute, the
bar coalgebra is cocommutative (coLie $\to$ Sym), and the Koszul
dual is $\mathrm{Sym}^{\mathrm{ch}}(V^*)$.  In both cases, it is
the \emph{statistics of the generators}, not the pole order, that
determines the operadic type.

\begin{theorem}[Free fermion bar complex; see
Theorem~\ref{thm:fermion-bar-complex-genus-0}; \ClaimStatusProvedElsewhere]
\label{thm:frame-fermion-bar}
The bar complex $\barB(\mathcal{F})$ of the free fermion is acyclic:
$H^n(\barB(\mathcal{F})) = 0$ for $n \geq 1$, with
$H^0 = \mathbb{C}$.  In particular, $\mathcal{F}$ is chiral Koszul.
\end{theorem}

Acyclicity is the strongest form of the Koszul property: no
cohomological obstruction at any degree.  For Heisenberg,
$H^2(\barB(\mathcal{H}_k)) = \mathbb{C} \cdot c_k \neq 0$
(Theorem~\ref{thm:frame-heisenberg-bar}) --- the double-pole
curvature creates a class that obstructs acyclicity.  The free
fermion, having only a simple pole, has no such obstruction.

\medskip
\noindent\textbf{The Koszul dual: the $\beta\gamma$ system.}
The Koszul dual of the free fermion is the $\beta\gamma$ system,
a chiral algebra with two bosonic generators $\beta(z)$ of
weight~$1$ and $\gamma(z)$ of weight~$0$.  Compute the OPE
directly:
\begin{equation}\label{eq:frame-betagamma-ope}
\beta(z)\,\gamma(w) = \frac{1}{z-w} + \text{regular},
\qquad
\gamma(z)\,\beta(w) = \frac{-1}{z-w} + \text{regular}.
\end{equation}
The pole order is $1$ --- the same as the fermion.  But the
generators $\beta, \gamma$ are bosonic: the sign flip in the
second OPE comes from the \emph{symplectic pairing}
$\langle \beta, \gamma \rangle = -\langle \gamma, \beta \rangle$,
not from fermionic statistics.  The bar coalgebra of the
$\beta\gamma$ system is cocommutative (bosonic generators),
and its coproduct encodes the commutative (symmetric) product
structure.  Dualizing gives $(\beta\gamma)^! = \mathcal{F}$:
Koszul duality exchanges
$\mathrm{Com} \leftrightarrow \mathrm{Lie}$
by exchanging statistics.

The following table records the data governing the bar complex
and the Koszul dual for all three free-field systems.  The
operadic type is determined by the row ``Statistics,'' not by
``OPE poles'':
\begin{center}
\small
\begin{tabular}{c|c|c|c}
& \textbf{Heisenberg} $\mathcal{H}_k$ &
\textbf{Free fermion} $\mathcal{F}$ &
\textbf{$\beta\gamma$ system} \\
\hline
Generators & $1$ (bosonic) & $1$ (fermionic) & $2$ (bosonic) \\
Statistics & bosonic & fermionic & bosonic \\
OPE poles & double ($1/(z{-}w)^2$) & simple ($1/(z{-}w)$) &
  simple ($1/(z{-}w)$) \\
Bar coalgebra & cocommutative & co-antisymmetric &
  cocommutative \\
Operadic type & $\chirCom$ & $\chirLie$ & $\chirCom$ \\
Bar differential & $d_{\mathrm{residue}}$ only
  & $d_{\mathrm{bracket}}$ only
  & $d_{\mathrm{bracket}}$ (mixed pairs) \\
Koszul dual & $\mathrm{Sym}^{\mathrm{ch}}(V^*)$
  & $\beta\gamma$ & $\mathcal{F}$ \\
\end{tabular}
\end{center}

The free-field examples expose the two independent axes of the
bar complex.  The bar differential of any augmented chiral
algebra decomposes as
$d = d_{\mathrm{bracket}} + d_{\mathrm{residue}}$: the
bracket component from simple poles, the curvature component
from double poles.  Heisenberg has $d_{\mathrm{bracket}} = 0$;
the free fermion has $d_{\mathrm{residue}} = 0$.
The general case --- affine Kac--Moody algebras --- has both,
and neither is individually a differential.

% ================================================================
\section{\texorpdfstring{The non-abelian world: affine $\widehat{\mathfrak{sl}}_2$}{The non-abelian world: affine sl2}}
\label{sec:frame-nonabelian-preview}
% ================================================================

The Heisenberg algebra has a single current with a double-pole
self-OPE and no simple pole.  The simplest non-abelian chiral
algebra, $\widehat{\mathfrak{sl}}_2$ at level~$k$, has three
currents $e(z), f(z), h(z)$ with OPE:
\begin{align}
e(z)\, f(w) &\sim \frac{h(w)}{z-w}
  + \frac{k}{(z-w)^2}, \label{eq:frame-sl2-ef} \\
h(z)\, e(w) &\sim \frac{2e(w)}{z-w}, \qquad
h(z)\, f(w) \sim \frac{-2f(w)}{z-w},
  \label{eq:frame-sl2-he-hf} \\
h(z)\, h(w) &\sim \frac{2k}{(z-w)^2}.
  \label{eq:frame-sl2-hh}
\end{align}

The simple poles in~\eqref{eq:frame-sl2-ef}--\eqref{eq:frame-sl2-he-hf}
are the new feature.  They contribute a
\emph{bracket component} $d_{\mathrm{bracket}}$ to the bar
differential, which was identically zero for Heisenberg.

\subsection{\texorpdfstring{The bar differential at degrees $0$--$2$}{The bar differential at degrees 0--2}}
\label{subsec:frame-sl2-bar-low-degree}

We repeat the Heisenberg computation of \S\ref{sec:frame-bar-deg1}--\S\ref{sec:frame-bar-deg2} for $\widehat{\mathfrak{sl}}_2$, emphasizing what changes.

\subsubsection*{Degree $0$}
The degree-$0$ bar space is $\bar{B}_0^{\mathrm{ch}} = \mathbb{C}$,
as before: the augmentation ideal modulo products.

\subsubsection*{Degree $1$: two types of pole}
A degree-$1$ element now involves two currents from $\{e, f, h\}$
and a single logarithmic form $\eta_{12}$.  The bar differential
$d = d_{\mathrm{bracket}} + d_{\mathrm{residue}}$ has two
components, one for each pole order.

\medskip\noindent\textbf{Simple-pole component $d_{\mathrm{bracket}}$.}
The OPE $h(z)\,e(w) \sim 2e(w)/(z-w)$ has a simple pole with
residue $c_1(w) = 2e(w)$.  The bar differential extracts this as
\begin{equation}\label{eq:frame-sl2-dbracket-deg1}
d_{\mathrm{bracket}}\bigl(
  s^{-1}h(z_1) \otimes s^{-1}e(z_2) \otimes \eta_{12}
\bigr)
= c_1(z_2) = 2e(z_2).
\end{equation}
This is the Lie bracket $[h, e] = 2e$ encoded in OPE language.
Contrast with Heisenberg, where $c_1 = 0$ and $d_{\mathrm{bracket}}$
vanishes identically.  For the full $\mathfrak{sl}_2$ system,
$d_{\mathrm{bracket}}$ on degree-$1$ elements recovers the
Chevalley--Eilenberg differential of $\mathfrak{sl}_2$:
\begin{equation}\label{eq:frame-sl2-ce-table}
\begin{aligned}
d_{\mathrm{bracket}}(h \otimes e \otimes \eta) &= 2e, &\qquad
d_{\mathrm{bracket}}(h \otimes f \otimes \eta) &= -2f, \\
d_{\mathrm{bracket}}(e \otimes f \otimes \eta) &= h, &\qquad
d_{\mathrm{bracket}}(h \otimes h \otimes \eta) &= 0.
\end{aligned}
\end{equation}

\medskip\noindent\textbf{Double-pole component $d_{\mathrm{residue}}$.}
The double poles $h(z)\,h(w) \sim 2k/(z-w)^2$ and
$e(z)\,f(w) \sim k/(z-w)^2 + \cdots$ contribute a curvature component:
\begin{equation}\label{eq:frame-sl2-dresid-deg1}
\begin{aligned}
d_{\mathrm{residue}}(h \otimes h \otimes \eta) &= 2k, \\
d_{\mathrm{residue}}(e \otimes f \otimes \eta) &= k, \\
d_{\mathrm{residue}}(h \otimes e \otimes \eta) &= 0.
\end{aligned}
\end{equation}
This is the Killing form $\kappa(J^a, J^b) = k \cdot (J^a, J^b)$
in OPE language, identical in structure to the Heisenberg double-pole
extraction.

The full bar differential is $d = d_{\mathrm{bracket}} + d_{\mathrm{residue}}$.
At degree~$1$:
\begin{equation}\label{eq:frame-sl2-full-d-deg1}
d(e \otimes f \otimes \eta) = \underbrace{h}_{\text{bracket}} + \underbrace{k}_{\text{curvature}}, \qquad
d(h \otimes h \otimes \eta) = \underbrace{0}_{\text{bracket}} + \underbrace{2k}_{\text{curvature}}.
\end{equation}

\subsubsection*{Degree $2$: the Jacobi failure}

At degree~$2$, we have three currents and two logarithmic forms
$\eta_{12} \wedge \eta_{23}$.  The bracket component
$d_{\mathrm{bracket}}$ now applies a Lie bracket to two of the
three currents via a simple-pole extraction, producing a degree-$1$
element.  Consider:
\begin{equation}\label{eq:frame-sl2-deg2-element}
\xi = e(z_1) \otimes h(z_2) \otimes f(z_3)
  \otimes \eta_{12} \wedge \eta_{23}.
\end{equation}
The bracket component extracts simple poles at each collision:
\begin{align}
\partial_{D_{12}}^{\mathrm{bracket}}(\xi)
  &= [e, h](z_{12}) \otimes f(z_3) \otimes \eta_{23}
  = -2e(z_{12}) \otimes f(z_3) \otimes \eta_{23},
\label{eq:frame-sl2-D12-bracket} \\
\partial_{D_{23}}^{\mathrm{bracket}}(\xi)
  &= -e(z_1) \otimes [h, f](z_{23}) \otimes \eta_{12}
  = +2e(z_1) \otimes f(z_{23}) \otimes \eta_{12},
\label{eq:frame-sl2-D23-bracket}
\end{align}
where the sign in~\eqref{eq:frame-sl2-D23-bracket} comes from the
wedge reordering $\eta_{12} \wedge \eta_{23}
= -\eta_{23} \wedge \eta_{12}$, as in the Heisenberg computation
of \S\ref{sec:frame-bar-deg2}.

Now apply $d_{\mathrm{bracket}}$ again.  From~\eqref{eq:frame-sl2-D12-bracket}:
\[
d_{\mathrm{bracket}}\bigl(-2e \otimes f \otimes \eta_{23}\bigr)
= -2h.
\]
From~\eqref{eq:frame-sl2-D23-bracket}:
\[
d_{\mathrm{bracket}}\bigl(2e \otimes f \otimes \eta_{12}\bigr)
= 2h.
\]
These would cancel if $d_{\mathrm{bracket}}$ were a differential.
But we have neglected the $D_{13}$ stratum (the $e$--$f$ collision),
which contributes via $[e, f] = h$:
\begin{equation}\label{eq:frame-sl2-D13-bracket}
\partial_{D_{13}}^{\mathrm{bracket}}(\xi)
= h(z_{13}) \otimes h(z_2) \otimes \eta_{12}|_{D_{13}}.
\end{equation}
After careful sign accounting (the form $\eta_{12}\wedge\eta_{23}$
restricts to $D_{13}$ non-trivially, unlike the Heisenberg case),
the three terms of $d_{\mathrm{bracket}}^2$ on $\xi$ do \emph{not}
cancel.  The residual term is proportional to $k$: it is precisely
the double-pole contribution from the $e$--$f$ OPE that the
bracket component ignores.

\begin{remark}[Why \texorpdfstring{$d_{\mathrm{bracket}}^2 \neq 0$}{d\_bracket\textasciicircum 2 != 0}]
\label{rem:frame-why-dbracket-fails}
In the classical bar complex of $U(\mathfrak{g})$, the
Chevalley--Eilenberg differential satisfies
$d_{\mathrm{CE}}^2 = 0$ by the Jacobi identity.  In the chiral
setting, $d_{\mathrm{bracket}}$ extracts simple poles, but the
Borcherds identity couples simple and double poles:
the ``Jacobi'' relation $[e, [h, f]] - [h, [e, f]] - [[e,h], f] = 0$
holds only when the double-pole (level-$k$) terms are included.
The full differential $d = d_{\mathrm{bracket}} + d_{\mathrm{residue}}$
satisfies $d^2 = 0$ via the complete Borcherds identity, which
intertwines both pole orders.  This is the chiral Koszul phenomenon:
the two components of $d$ are individually \emph{not} differentials;
they form a differential only in combination
(\S\ref{sec:selection-principle}).
\end{remark}

\subsection{\texorpdfstring{$d_{\mathrm{bracket}}^2 \neq 0$}{d bracket squared is not zero}}

For $\widehat{\mathfrak{sl}}_2$, the bracket component
$d_{\mathrm{bracket}}$ alone does \emph{not} satisfy
$d_{\mathrm{bracket}}^2 = 0$.  This is proved computationally:
all $2048$ sign conventions for the bar differential have been
verified to give $d_{\mathrm{bracket}}^2 \neq 0$
(see Theorem~\ref{thm:pbw-koszulness-criterion}).
The combined differential $d = d_{\mathrm{bracket}}
+ d_{\mathrm{curvature}}$ satisfies $d^2 = 0$ by the full
Borcherds identity (which involves both simple and double poles),
not by the Jacobi identity alone.

The difference between classical and chiral
Koszul duality.  In the classical setting, the enveloping algebra
$U(\mathfrak{g})$ is Koszul (BGS~\cite{BGS96}), and the bar
differential $d_{\mathrm{CE}} = d_{\mathrm{bracket}}$ satisfies
$d_{\mathrm{CE}}^2 = 0$ by the Jacobi identity.  In the chiral
setting, $\widehat{\mathfrak{g}}_k$ uses all OPE poles (the full
Borcherds identity), and the bracket-only piece is not a
differential on its own.

\subsection{The PBW spectral sequence}

The correct computational tool is the \emph{PBW spectral sequence}.
Filter the bar complex by conformal weight.  The associated graded
is the classical bar complex of $U(\mathfrak{g})$, which \emph{is}
a chain complex (with differential $d_{\mathrm{CE}}$).  The
spectral sequence has:
\begin{itemize}
\item $E_1$ page: the bar complex of $U(\mathfrak{g})$ with
  $d_{\mathrm{CE}}$.
\item $E_2$ page: the Chevalley--Eilenberg cohomology
  $H^*_{\mathrm{CE}}(\mathfrak{g}, \mathbb{C})$.
\end{itemize}
For Koszul algebras, the spectral sequence collapses at~$E_2$,
giving the chiral bar cohomology.  The proof that
$\widehat{\mathfrak{g}}_k$ is chiral Koszul uses PBW flatness
of the associated graded together with the classical Koszulness
of $U(\mathfrak{g})$ (Priddy~\cite{Priddy70}); see
Theorem~\ref{thm:pbw-koszulness-criterion}.

\subsection{The Feigin--Frenkel involution as Koszul duality}

The Koszul dual of $\widehat{\mathfrak{g}}_k$ is
$\widehat{\mathfrak{g}}_{-k-2h^\vee}$, where $h^\vee$ is the
dual Coxeter number (Theorem~\ref{thm:universal-kac-moody-koszul}).
For $\mathfrak{g} = \mathfrak{sl}_2$, $h^\vee = 2$ and the duality
sends $k \mapsto -k - 4$.

\begin{center}
\small
\begin{tabular}{c|c|c}
& \textbf{Heisenberg} $\mathcal{H}_k$ &
\textbf{Kac--Moody} $\widehat{\mathfrak{g}}_k$ \\
\hline
Bracket & Abelian ($d_{\mathrm{bracket}} = 0$)
  & Non-abelian ($d_{\mathrm{bracket}} \neq 0$) \\
$d^2 = 0$ from & Arnold alone
  & Full Borcherds identity \\
Spectral sequence & Trivial ($E_1 = E_\infty$)
  & PBW ($E_2$ collapse for Koszul) \\
Koszul dual & $\mathrm{Sym}^{\mathrm{ch}}(V^*)$
  & $\widehat{\mathfrak{g}}_{-k-2h^\vee}$ \\
Level shift & None ($h^\vee = 0$)
  & $k \mapsto -k - 2h^\vee$ \\
Discriminant & $\Delta(x) = 1$
  & $\Delta(x) = (1-3x)(1+x)$ for $\mathfrak{sl}_2$ \\
Critical level & $k = 0$ (degenerate)
  & $k = -h^\vee$ (curvature vanishes)
\end{tabular}
\end{center}

At the critical level $k = -h^\vee$, the curvature of the bar
complex vanishes: $d^2 = 0$ at all genera.  This is the level at
which the center of $\widehat{\mathfrak{g}}_k$ becomes large
(the Feigin--Frenkel center $\mathfrak{z}(\widehat{\mathfrak{g}}_{-h^\vee})
\cong \mathcal{W}(\widehat{\mathfrak{g}}^\vee)$), and the bar
complex recovers the Langlands dual.

The Feigin--Frenkel involution $k \leftrightarrow -k - 2h^\vee$
is not a representation-theoretic accident: it is Koszul duality
in the chiral algebra sense, proved in
Theorem~\ref{thm:universal-kac-moody-koszul} via Verdier duality
on Fulton--MacPherson configuration spaces.

% ================================================================
\section{The nonabelian Rosetta Stone: reading the full structure
from \texorpdfstring{$\widehat{\mathfrak{sl}}_2$}{affine sl2}}
\label{sec:rosetta-sl2}
% ================================================================

The Heisenberg algebra is abelian: its OPE has only a double pole,
its bar differential has only $d_{\mathrm{curvature}}$, and all
higher operations vanish.  The affine Kac--Moody algebra
$\widehat{\mathfrak{sl}}_{2,k}$ is the first example where the full
structure is genuinely nontrivial.  The OPE has \emph{both} simple
poles (from the Lie bracket) and double poles (from the Killing form),
the bar differential decomposes as
$d = d_{\mathrm{bracket}} + d_{\mathrm{curvature}}$ with
$d_{\mathrm{bracket}}^2 \neq 0$, and the Feigin--Frenkel involution
$k \mapsto -k-4$ emerges as Verdier duality on configuration spaces.

Three structures emerge that were invisible for Heisenberg:
\begin{enumerate}
\item The \emph{Swiss-cheese decomposition} of the bar complex into
  holomorphic (closed-color) and topological (open-color) components,
  with the curvature obstruction to flatness of the closed-color
  structure alone.
\item The \emph{affine Poisson vertex algebra} structure on bar
  cohomology, with the Jacobi identity verified directly from the
  Arnold relation.
\item The \emph{Feigin--Frenkel involution as Verdier duality}:
  the classical involution $k \mapsto -k - 2h^\vee$ is not an
  ad hoc symmetry of level but the action of Verdier duality on the
  bar differential, exchanging the roles of simple and double poles.
\end{enumerate}


% ----------------------------------------------------------------
\subsection{The OPE and bar complex in the sl\textsubscript{2} frame}
\label{subsec:rosetta-sl2-bar}
% ----------------------------------------------------------------

We recall the data (Definition at line~\eqref{eq:frame-sl2-ef}):
three generators $e, f, h$ with the $\mathfrak{sl}_2$ OPE
\begin{align}
e(z)\,f(w) &\sim \frac{k}{(z-w)^2} + \frac{h(w)}{z-w},
  \label{eq:rosetta-ef}\\
h(z)\,e(w) &\sim \frac{2e(w)}{z-w}, \qquad
h(z)\,f(w) \sim \frac{-2f(w)}{z-w},
  \label{eq:rosetta-he-hf}\\
h(z)\,h(w) &\sim \frac{2k}{(z-w)^2}.
  \label{eq:rosetta-hh}
\end{align}
All remaining OPEs ($e$--$e$, $f$--$f$) are regular.

The bar complex at each degree is:
\begin{itemize}
\item \emph{Degree $0$.}
  $\barB^0 = \mathbb{C}$ (the vacuum).

\item \emph{Degree $1$.}
  $\barB^1 = \mathfrak{sl}_2^{\otimes 2} \otimes
  \Omega^1_{\log}(\overline{C}_2)$, with basis elements
  $J^a \otimes J^b \otimes \eta_{12}$ for $a, b \in \{e, f, h\}$.
  The space has dimension $3^2 = 9$ as a vector space of coefficient
  tensors (before imposing the bar-complex grading), but the augmented
  bar-complex grading identifies the nine entries with the
  nine structure/Killing components of $\mathfrak{sl}_2$.

\item \emph{Degree $2$.}
  $\barB^2 = \mathfrak{sl}_2^{\otimes 3} \otimes
  \Omega^2_{\log}(\overline{C}_3)$, with elements of the form
  $J^a \otimes J^b \otimes J^c \otimes \eta_{12} \wedge \eta_{23}$.
\end{itemize}

The bar differential $d\colon \barB^n \to \barB^{n-1}$ extracts
residues at all collision divisors, with one component for each pole
order:
\begin{equation}\label{eq:rosetta-d-decomposition}
d = d_{\mathrm{bracket}} + d_{\mathrm{curvature}}.
\end{equation}
The bracket component $d_{\mathrm{bracket}}$ extracts simple-pole
residues (the Lie bracket $[J^a, J^b] = f^{ab}{}_c\, J^c$); the
curvature component $d_{\mathrm{curvature}}$ extracts double-pole
residues (the Killing form $k \cdot \kappa(J^a, J^b)$).  The
extraction table at degree~$1$ is the content of
equations~\eqref{eq:frame-sl2-dbracket-deg1}--\eqref{eq:frame-sl2-dresid-deg1}:
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{l|c|c|c}
\textbf{Element} & $d_{\mathrm{bracket}}$
  & $d_{\mathrm{curvature}}$ & $d = d_{\mathrm{bracket}} + d_{\mathrm{curvature}}$ \\
\hline
$h \otimes e \otimes \eta$ & $2e$ & $0$ & $2e$ \\
$h \otimes f \otimes \eta$ & $-2f$ & $0$ & $-2f$ \\
$e \otimes f \otimes \eta$ & $h$ & $k$ & $h + k$ \\
$h \otimes h \otimes \eta$ & $0$ & $2k$ & $2k$
\end{tabular}
\end{center}
The first column is the Chevalley--Eilenberg differential of
$\mathfrak{sl}_2$; the second column is the Heisenberg-type curvature
(a multiple of the Killing form); the third column is the full chiral
bar differential.

\begin{remark}[The two components have different geometric origins]
\label{rem:rosetta-two-components}
The bracket component $d_{\mathrm{bracket}}$ extracts
$\Res_{z_1 = z_2}[c_1(z_2)/(z_1 - z_2)]$, the coefficient of
the simple pole in the OPE.  The curvature component
$d_{\mathrm{curvature}}$ extracts
$\Res_{z_1 = z_2}[c_2/(z_1 - z_2)^2]$, the coefficient of the
double pole.  On the Fulton--MacPherson compactification
$\FM_2(\mathbb{C})$, these correspond to the first and second
boundary jet of the logarithmic form $\eta_{12}$ along the diagonal
$D_{12}$.  The simple pole contributes to $\partial\FM_2$ at
first order; the double pole requires the exceptional fiber
direction of the blowup.
\end{remark}

The degree-$2$ analysis of
\S\ref{subsec:frame-sl2-bar-low-degree} shows that
$d_{\mathrm{bracket}}^2 \neq 0$ on the element
$\xi = e \otimes h \otimes f \otimes \eta_{12} \wedge \eta_{23}$
(Remark~\ref{rem:frame-why-dbracket-fails}).  The full differential
$d^2 = 0$ is restored only when both components are present, via
the Borcherds identity.


% ----------------------------------------------------------------
\subsection{Swiss-cheese decomposition}
\label{subsec:rosetta-swiss-cheese}
% ----------------------------------------------------------------

The bar complex of any chiral algebra carries a two-colored
(Swiss-cheese) structure in which the holomorphic bar differential
and the topological coproduct occupy independent directions
(Theorem~\ref{thm:bar-swiss-cheese}).  For Heisenberg, the
holomorphic direction is automatically flat
($d_{\mathrm{curvature}}^2 = 0$ since the bracket vanishes), and
the Swiss-cheese structure is a direct product of a cochain complex
with a coalgebra.  For $\widehat{\mathfrak{sl}}_2$, the holomorphic
direction acquires a genuine obstruction.

\begin{theorem}[$\mathfrak{sl}_2$ bar complex as Swiss-cheese
coalgebra; \ClaimStatusProvedHere]
\label{thm:rosetta-sl2-swiss}
The bar complex $\barB(\widehat{\mathfrak{sl}}_{2,k})$, equipped
with its bar differential $d = d_{\mathrm{bracket}}
+ d_{\mathrm{curvature}}$ and deconcatenation coproduct~$\Delta$,
is a dg coalgebra over the holomorphic--topological Swiss-cheese
operad $\mathsf{SC}^{\mathrm{ch,top}}$
\textup{(Definition~\ref{def:SC})}:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Closed color\textup{:}} the differential
  $d = d_{\mathrm{bracket}} + d_{\mathrm{curvature}}$
  is parametrized by the Fulton--MacPherson space $\FM_n(\mathbb{C})$.
  Individually, $d_{\mathrm{bracket}}^2 \neq 0$; the curvature term
  $d_{\mathrm{curvature}}$ is needed to complete
  $d^2 = 0$.
\item \emph{Open color\textup{:}} the deconcatenation
  coproduct~$\Delta$ is parametrized by $\Conf_n(\mathbb{R})$,
  giving the $\Eone$-coalgebra structure.
\item \emph{Compatibility\textup{:}} $d$ is a coderivation
  of~$\Delta$.  The holomorphic ($\mathbb{C}$) and topological
  ($\mathbb{R}$) directions are independent.
\end{enumerate}
\end{theorem}

\begin{proof}
The proof is the same as Theorem~\ref{thm:bar-swiss-cheese},
applied to $\cA = \widehat{\mathfrak{sl}}_{2,k}$.  The
deconcatenation coproduct
$\Delta[a_1|\cdots|a_n]
= \sum_{i=0}^{n} [a_1|\cdots|a_i] \otimes [a_{i+1}|\cdots|a_n]$
is the tensor coalgebra structure, coassociative by construction.
The differential~$d$ is a coderivation of~$\Delta$ because
collision residues in~$\mathbb{C}$ commute with interval splitting
in~$\mathbb{R}$: the Leibniz rule
$d \circ \Delta
= (\mathrm{id} \otimes d + d \otimes \mathrm{id}) \circ \Delta$
holds for both $d_{\mathrm{bracket}}$ (which extracts simple-pole
residues) and $d_{\mathrm{curvature}}$ (which extracts double-pole
residues), independently.
\end{proof}

\begin{remark}[The new feature: curvature obstruction to
holomorphic flatness]
\label{rem:rosetta-sl2-curvature-obstruction}
For Heisenberg, the closed-color structure is flat:
$d = d_{\mathrm{curvature}}$ (no bracket), and
$d_{\mathrm{curvature}}^2 = 0$ since the bar differential of any
commutative (abelian) algebra squares to zero on its own.  For
$\widehat{\mathfrak{sl}}_2$, the closed-color structure is
\emph{not flat by itself}: $d_{\mathrm{bracket}}^2 \neq 0$
(the Chevalley--Eilenberg differential of $\mathfrak{sl}_2$ does
square to zero classically, but in the chiral setting the simple-pole
extraction misses the double-pole terms required by the Borcherds
identity).  The curvature component $d_{\mathrm{curvature}}$ is
the correction that completes $d^2 = 0$.

In Swiss-cheese language: the closed-color differential has a
\emph{curvature defect} that is cancelled by the level-dependent
piece.  This is a genuinely non-abelian phenomenon, invisible for
Heisenberg.
\end{remark}


% ----------------------------------------------------------------
\subsection{Reading off $m_2$ and the Feigin--Frenkel involution}
\label{subsec:rosetta-operations}
% ----------------------------------------------------------------

The bar complex encodes the $\Ainf$ operations of
$\widehat{\mathfrak{sl}}_2$ by residue extraction.  The binary
product $m_2$ is read from the degree-$1$ bar differential.

\begin{proposition}[The $m_2$ operation; \ClaimStatusProvedHere]
\label{prop:rosetta-sl2-m2}
The binary $\Ainf$ operation on bar generators is:
\begin{equation}\label{eq:rosetta-m2}
m_2(J^a, J^b) = f^{ab}{}_c\, J^c + k\, \kappa^{ab}
\end{equation}
where $f^{ab}{}_c$ are the $\mathfrak{sl}_2$ structure constants and
$\kappa^{ab} = (J^a, J^b)$ is the normalized invariant bilinear form.
In the lambda-bracket language\textup{:}
\begin{equation}\label{eq:rosetta-lambda-bracket}
\{J^a {}_\lambda J^b\} = f^{ab}{}_c\, J^c + k\, \kappa^{ab}\, \lambda.
\end{equation}
The $\lambda^0$ coefficient is the Lie bracket; the $\lambda^1$
coefficient is the Killing form.
\end{proposition}

\begin{proof}
The degree-$1$ bar differential
$d(J^a \otimes J^b \otimes \eta_{12})$ extracts
$\Res_{z_1 = z_2}[J^a(z_1) J^b(z_2) \cdot \eta_{12}]$.  The
OPE~\eqref{eq:rosetta-ef}--\eqref{eq:rosetta-hh} has the form
$J^a(z) J^b(w) \sim k\, \kappa^{ab}/(z-w)^2
+ f^{ab}{}_c\, J^c(w)/(z-w)$, so the residue picks up both the
simple-pole coefficient $f^{ab}{}_c\, J^c$ (the Lie bracket) and
the double-pole coefficient $k\, \kappa^{ab}$ (the level).  The
lambda-bracket~\eqref{eq:rosetta-lambda-bracket} encodes both in a
single polynomial in~$\lambda$: the double pole contributes the
$\lambda^1$ term.
\end{proof}

\begin{remark}[Comparison with Heisenberg]
For the Heisenberg algebra, $m_2(\alpha, \alpha) = k$ (pure
curvature, no bracket) and $\{\alpha {}_\lambda \alpha\} = k\lambda$.
For $\widehat{\mathfrak{sl}}_2$, the $\lambda^0$ term is new: it
encodes the non-abelian Lie structure.  The lambda-bracket is the
\emph{affine Poisson vertex algebra} (affine PVA) associated to
$\mathfrak{sl}_2$ at level~$k$.
\end{remark}

\medskip
\noindent\textbf{The Feigin--Frenkel involution from Verdier duality.}

Verdier duality on $\FM_n(\mathbb{C})$ exchanges logarithmic forms
with distributional currents
(Theorem~\ref{thm:bar-cobar-verdier}; \S\ref{sec:geometric-arena}).
On the bar complex, it acts on the \emph{coefficients} of the
differential.

\begin{theorem}[Feigin--Frenkel involution as Verdier duality;
\ClaimStatusProvedHere]
\label{thm:rosetta-feigin-frenkel}
Verdier duality on $\FM_n(\mathbb{C})$ induces an isomorphism of
bar complexes\textup{:}
\begin{equation}\label{eq:rosetta-verdier-km}
\mathbb{D}\colon
\barB(\widehat{\mathfrak{sl}}_{2,k})
\;\xrightarrow{\;\sim\;}\;
\barB(\widehat{\mathfrak{sl}}_{2,{-k-4}})^\vee.
\end{equation}
The level shift $k \mapsto -k - 2h^\vee = -k - 4$ is the
Feigin--Frenkel involution, realized geometrically.
\end{theorem}

\begin{proof}
Verdier duality exchanges the logarithmic propagator
$\eta_{12} = d\log(z_1 - z_2)$ with the distributional current
$\delta_{12} = \delta(z_1 - z_2)\, dz_1 \wedge d\bar{z}_2$, paired
by $\langle \eta_{12}, \delta_{12} \rangle = 1$.  On the bar
differential:

\emph{Bracket component.}
$d_{\mathrm{bracket}}$ extracts simple-pole residues with
coefficients $f^{ab}{}_c$.  The structure constants are antisymmetric
($f^{ab}{}_c = -f^{ba}{}_c$) and the Verdier dual of a simple-pole
residue is a simple-pole residue with the same coefficient.  The Lie
algebra $\mathfrak{sl}_2$ is self-dual
($\mathfrak{sl}_2 \cong \mathfrak{sl}_2^*$ via the Killing form),
so the structure constants are preserved under duality.

\emph{Curvature component.}
$d_{\mathrm{curvature}}$ extracts double-pole residues with
coefficient $k \cdot \kappa^{ab}$.  The Verdier dual of the
double-pole extraction on $\FM_2(\mathbb{C})$ acts by the
substitution
\[
k \longmapsto -k - 2h^\vee.
\]
This shift arises as follows.  The logarithmic pairing
$\langle \eta_{12}^{\wedge 2}, \delta_{12} \rangle$ on
$\overline{C}_2(\mathbb{C})$ produces a normalization that
differs from the distributional pairing by the
\emph{adjoint trace}: $\operatorname{Tr}(\mathrm{ad}_{J^a} \circ \mathrm{ad}_{J^b})
= 2h^\vee \cdot \kappa^{ab}$.  For $\mathfrak{sl}_2$,
$2h^\vee = 4$ and $\operatorname{Tr}(\mathrm{ad}_e \circ \mathrm{ad}_f) = 4$
(since the adjoint representation has dimension~$3$ and the
eigenvalues of $\mathrm{ad}_h$ are $\pm 2$ and~$0$).  The Verdier
duality formula on the double-pole coefficient is therefore
\[
\mathbb{D}(k \cdot \kappa^{ab})
= (-k - 2h^\vee) \cdot \kappa^{ab},
\]
and the dual bar complex has level $-k - 4$.

Combining both components: the dual bar complex has the same
structure constants $f^{ab}{}_c$ (preserved) and level $-k - 4$
(shifted), hence is $\barB(\widehat{\mathfrak{sl}}_{2,-k-4})^\vee$.
\end{proof}

\begin{remark}[Critical level as Verdier fixed point]
\label{rem:rosetta-critical}
The critical level $k = -h^\vee = -2$ is the unique fixed point
of $k \mapsto -k - 4$: the bar complex is Verdier self-dual, the
curvature vanishes ($m_0 = 0$), and the Koszul dual is
$\widehat{\mathfrak{sl}}_{2,-2}$ itself.  This is the geometric
content of the Feigin--Frenkel theorem at critical level
(Theorem~\ref{thm:critical-level-structure}).
\end{remark}


% ----------------------------------------------------------------
\subsection{The affine PVA and Jacobi from the Arnold relation}
\label{subsec:rosetta-pva}
% ----------------------------------------------------------------

The bar cohomology of $\widehat{\mathfrak{sl}}_{2,k}$ at genus~$0$
carries the structure of a \emph{Poisson vertex algebra} (PVA).
This is the ``shadow'' ($S$-level) of the full chiral bar-cobar
duality, obtained by passing to cohomology.

\begin{proposition}[Affine PVA from bar cohomology;
\ClaimStatusProvedHere]
\label{prop:rosetta-sl2-pva}
The genus-$0$ bar cohomology
$H^*(\barB(\widehat{\mathfrak{sl}}_{2,k}))$ carries a PVA structure
with generators $e, f, h$ and lambda-bracket\textup{:}
\begin{equation}\label{eq:rosetta-pva-bracket}
\{e {}_\lambda f\} = h + k\lambda, \qquad
\{h {}_\lambda e\} = 2e, \qquad
\{h {}_\lambda f\} = -2f, \qquad
\{h {}_\lambda h\} = 2k\lambda.
\end{equation}
All remaining brackets \textup{(}$\{e {}_\lambda e\}$,
$\{f {}_\lambda f\}$\textup{)} vanish.  This is the affine PVA
associated to $\mathfrak{sl}_2$ at level~$k$.
\end{proposition}

\begin{proof}
The lambda-bracket is read from the OPE:
$J^a(z) J^b(w) \sim c_0^{ab}(w)/(z-w) + c_1^{ab}/(z-w)^2$ gives
$\{J^a {}_\lambda J^b\} = c_0^{ab} + c_1^{ab}\lambda$.  Applying
this to~\eqref{eq:rosetta-ef}--\eqref{eq:rosetta-hh} produces the
brackets~\eqref{eq:rosetta-pva-bracket}.  The product is the
commutative vertex algebra product (normal-ordered product).
\end{proof}

The PVA axioms require \emph{skew-symmetry} and the \emph{Jacobi
identity}.  Skew-symmetry in the PVA sense is:
$\{a {}_\lambda b\} = -\{b {}_{-\lambda - \partial} a\}$, where
$\partial$ acts as the derivation $T = L_{-1}$ (translation
operator) on the target.  On generators (which are primary of
conformal weight~$1$), $\partial$ acts by formal differentiation
and $\partial \cdot 1 = 0$.

We verify the Jacobi identity on the triple $(e, f, h)$, the only
non-trivial case (all triples involving $e$--$e$ or $f$--$f$ are
trivially zero).

\begin{proposition}[PVA Jacobi identity for
$\widehat{\mathfrak{sl}}_{2,k}$; \ClaimStatusProvedHere]
\label{prop:rosetta-jacobi}
The lambda-brackets~\eqref{eq:rosetta-pva-bracket} satisfy the PVA
Jacobi identity\textup{:}
\begin{equation}\label{eq:rosetta-pva-jacobi}
\{a {}_\lambda \{b {}_\mu c\}\}
- \{b {}_\mu \{a {}_\lambda c\}\}
= \{\{a {}_\lambda b\} {}_{\lambda+\mu} c\}
\end{equation}
for all $a, b, c \in \{e, f, h\}$.
\end{proposition}

\begin{proof}
We verify~\eqref{eq:rosetta-pva-jacobi} for the representative
triple $(a, b, c) = (e, f, h)$.  All other non-trivial triples
are obtained by permutation and the calculation is analogous.

\medskip
\emph{Step~1: Compute the skew-symmetric brackets.}
From~\eqref{eq:rosetta-pva-bracket},
$\{e {}_\lambda f\} = h + k\lambda$.  By PVA skew-symmetry:
\begin{equation}\label{eq:rosetta-skew-fe}
\{f {}_\mu e\}
= -\{e {}_{-\mu - \partial} f\}
= -(h + k(-\mu - \partial)) \cdot 1
= -h + k\mu.
\end{equation}
Similarly, $\{h {}_\lambda f\} = -2f$ gives
$\{f {}_\mu h\} = -\{h {}_{-\mu - \partial} f\}
= -(-2f) = 2f$, and $\{h {}_\lambda e\} = 2e$ gives
$\{e {}_\mu h\} = -\{h {}_{-\mu - \partial} e\} = -(2e) = -2e$.

\medskip
\emph{Step~2: Left side of the Jacobi identity.}

First term:
$\{e {}_\lambda \{f {}_\mu h\}\}
= \{e {}_\lambda (2f)\}
= 2\{e {}_\lambda f\}
= 2(h + k\lambda)
= 2h + 2k\lambda$.

Second term:
$\{f {}_\mu \{e {}_\lambda h\}\}
= \{f {}_\mu (-2e)\}
= -2\{f {}_\mu e\}
= -2(-h + k\mu)
= 2h - 2k\mu$.

The left side of~\eqref{eq:rosetta-pva-jacobi} is:
\begin{equation}\label{eq:rosetta-jacobi-lhs}
(2h + 2k\lambda) - (2h - 2k\mu) = 2k(\lambda + \mu).
\end{equation}

\medskip
\emph{Step~3: Right side of the Jacobi identity.}

We have $\{e {}_\lambda f\} = h + k\lambda$, so:
\begin{equation}\label{eq:rosetta-jacobi-rhs}
\{\{e {}_\lambda f\} {}_{\lambda+\mu} h\}
= \{(h + k\lambda) {}_{\lambda+\mu} h\}
= \{h {}_{\lambda+\mu} h\} + k\lambda \cdot 0
= 2k(\lambda + \mu).
\end{equation}
Here $k\lambda$ is a scalar (not a field), so
$\{k\lambda {}_{\lambda+\mu} h\} = 0$.

\medskip
\emph{Step~4: Verification.}

Comparing~\eqref{eq:rosetta-jacobi-lhs}
and~\eqref{eq:rosetta-jacobi-rhs}:
\[
2k(\lambda + \mu) = 2k(\lambda + \mu).
\]
The Jacobi identity is satisfied.
\end{proof}

\begin{remark}[Geometric origin of the Jacobi identity]
\label{rem:rosetta-jacobi-geometric}
The PVA Jacobi identity~\eqref{eq:rosetta-pva-jacobi} is the shadow
of the Arnold relation on $\overline{C}_3(\mathbb{P}^1)$.  The three
terms in the Jacobi identity correspond to the three collision
divisors $D_{12}$, $D_{23}$, $D_{13}$ in
$\partial\overline{C}_3(\mathbb{P}^1)$, and the identity
$\eta_{12} \wedge \eta_{23} + \eta_{23} \wedge \eta_{13}
+ \eta_{13} \wedge \eta_{12} = 0$
(Proposition~\ref{prop:frame-arnold}) forces the signed sum of
residue extractions to vanish.  For Heisenberg, each term involves
only double poles and the Jacobi identity reduces to the
commutativity $\kappa^{ab} = \kappa^{ba}$ of the Killing form.  For
$\widehat{\mathfrak{sl}}_2$, simple and double poles mix: the
Arnold relation must account for both pole orders simultaneously,
and this is what produces the level-dependent verification in
Proposition~\ref{prop:rosetta-jacobi}.
\end{remark}

\begin{remark}[From PVA to vertex algebra: quantization]
\label{rem:rosetta-quantization}
The affine PVA of Proposition~\ref{prop:rosetta-sl2-pva} is the
\emph{classical limit} of the vertex algebra
$\widehat{\mathfrak{sl}}_{2,k}$.  In the language of
Beilinson--Drinfeld, the PVA is a \emph{coisson algebra}: a
commutative chiral algebra equipped with a Poisson bracket from
the $\lambda$-bracket.  The vertex algebra is its quantization.
At the $S$-level, the bar cohomology computes the PVA; at the
$M$-level, the bar complex computes the full vertex algebra
structure, including all higher $\Ainf$ operations.  The passage
from the PVA ($S$-level) to the full vertex algebra ($M$-level)
is the chiral analog of the passage from a Poisson manifold to
its deformation quantization.
\end{remark}

\begin{remark}[The role of $d_{\mathrm{bracket}}^2 \neq 0$ in the
PVA picture]
\label{rem:rosetta-dbracket-pva}
The failure $d_{\mathrm{bracket}}^2 \neq 0$
(Remark~\ref{rem:frame-why-dbracket-fails}) is the chain-level
manifestation of the Lie bracket alone (the $\lambda^0$
coefficient of the lambda-bracket) does not define a PVA: the
Killing form ($\lambda^1$ coefficient) is required for the Jacobi
identity to hold in the PVA sense.  In the language of the PBW
spectral sequence (\S\ref{subsec:frame-sl2-bar-low-degree}), the
Chevalley--Eilenberg differential (which \emph{does} square to zero
classically) appears at the $E_1$ page; the double-pole correction
appears at the $E_2$ page; and the collapse at $E_2$ (for Koszul
algebras) means that the two-page computation is exact.
\end{remark}

\bigskip
\noindent\textbf{Summary: the nonabelian enrichment.}

The Heisenberg frame computes the full vertical structure (bar
complex, Arnold relation, Koszul dual, curvature, genus tower) for
an abelian algebra whose only OPE singularity is a double pole.
The $\widehat{\mathfrak{sl}}_2$ frame adds the \emph{horizontal
enrichment}: the simple pole, the Lie bracket, the PBW spectral
sequence, and the Feigin--Frenkel involution as Verdier duality.
Every computation in the Heisenberg frame has a non-abelian
counterpart in the $\mathfrak{sl}_2$ frame, with the bracket
component $d_{\mathrm{bracket}}$ as the new ingredient:

\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{l|c|c}
\textbf{Feature} & \textbf{Heisenberg $\mathcal{H}_k$}
  & $\widehat{\mathfrak{sl}}_{2,k}$ \\
\hline
OPE poles & double only & simple $+$ double \\
Bar differential & $d = d_{\mathrm{curvature}}$
  & $d = d_{\mathrm{bracket}} + d_{\mathrm{curvature}}$ \\
$d_{\mathrm{bracket}}^2$ & $= 0$ (trivially)
  & $\neq 0$ (Borcherds) \\
Lambda-bracket & $\{J {}_\lambda J\} = k\lambda$
  & $\{J^a {}_\lambda J^b\} = f^{ab}{}_c J^c + k\kappa^{ab}\lambda$ \\
PVA Jacobi & Commutativity of $\kappa$
  & Arnold $+$ both pole orders \\
Koszul dual & $\mathrm{Sym}^{\mathrm{ch}}(V^*)$
  & $\widehat{\mathfrak{sl}}_{2,-k-4}$ \\
Verdier action & $k \mapsto -k$
  & $k \mapsto -k - 4$ \\
Swiss-cheese & Flat closed color
  & Curved closed color (defect $= k$)
\end{tabular}
\end{center}

The passage from Heisenberg to $\widehat{\mathfrak{sl}}_2$ is the
simplest instance of the general pattern: Koszul duality for
non-abelian chiral algebras requires the full Borcherds identity,
not just the Arnold relation.  Every subsequent example
($\mathcal{W}$-algebras, Yangians) inherits this structure and adds
further layers.

% ================================================================
\subsection{The braided atom: abelian Chern--Simons and the spectral
$R$-matrix}
\label{subsec:rosetta-cs}
\index{Chern--Simons!abelian!R-matrix}
\index{R-matrix!spectral!abelian CS}
\index{Rosetta Stone!abelian Chern--Simons}
% ================================================================

\providecommand{\hh}{\hbar}

The Heisenberg algebra has only a double pole; affine Kac--Moody
has both simple and double poles.  What does a chiral algebra with
\emph{only a simple pole} look like?  The answer is
\emph{abelian Chern--Simons theory on $\bC \times \bR_{\ge 0}$},
whose boundary current algebra has a single generator~$J$ with the
OPE
\begin{equation}\label{eq:rosetta-cs-ope}
J(z)\,J(w) \;\sim\; \frac{k}{z - w}.
\end{equation}
This is a \emph{simple} pole---not the double pole of the Heisenberg
OPE~\eqref{eq:frame-heisenberg-ope}---and this single difference
propagates through the entire bar-complex dictionary: the bar
differential has $d_{\mathrm{bracket}} \neq 0$ and
$d_{\mathrm{curvature}} = 0$ at genus~$0$, the $\lambda$-bracket is
constant in~$\lambda$, and the theory carries a nontrivial spectral
$R$-matrix.

\medskip
\noindent\textbf{The $\lambda$-bracket.}\enspace
Because the OPE~\eqref{eq:rosetta-cs-ope} has only a simple pole,
the $\lambda$-bracket is the $\lambda^0$ coefficient:
\begin{equation}\label{eq:rosetta-cs-lambda-bracket}
\{J {}_\lambda J\} \;=\; k
\qquad
\text{(constant in $\lambda$)}.
\end{equation}
Compare with Heisenberg: the double pole gives
$\{J {}_\lambda J\} = k\lambda$ (linear in~$\lambda$), and with
affine Kac--Moody: the OPE $J^a(z)\,J^b(w) \sim
f^{ab}{}_c J^c(w)/(z-w) + k\kappa^{ab}/(z-w)^2$ gives
$\{J^a {}_\lambda J^b\} = f^{ab}{}_c J^c + k\kappa^{ab}\lambda$
(both constant and linear terms).

The $\lambda$-independence of~\eqref{eq:rosetta-cs-lambda-bracket}
has a bar-complex interpretation: the bar differential on
degree-$2$ elements extracts the simple-pole residue
\[
d_{\mathrm{bracket}}[s^{-1}J \,|\, s^{-1}J]
\;=\;
\Res_{z_1 = z_2}\!\Bigl[
  \frac{k}{z_1 - z_2}
  \cdot d\log(z_1 - z_2)
\Bigr]
\;=\;
\Res_{z_1 = z_2}\!\Bigl[
  \frac{k}{(z_1 - z_2)^2}\, dz_1
\Bigr]
\;=\; 0,
\]
but the value $m_2(J,J;\lambda) = k$ (constant) means the
bar differential carries the information as a \emph{degree-zero}
cocycle, not a spectral-parameter-dependent one.  The curvature
component $d_{\mathrm{curvature}}$, which extracts the double-pole
residue, vanishes identically at genus~$0$ because there is no
double pole.  This is the opposite of the Heisenberg case, where
$d_{\mathrm{bracket}} = 0$ and $d_{\mathrm{curvature}} \neq 0$.

\medskip
\noindent\textbf{The spectral $R$-matrix.}\enspace
The spectral $R$-matrix is obtained by the Laplace
transform of the $\lambda$-bracket
(the Laplace-transform formula of Volume~II):
\begin{equation}\label{eq:rosetta-cs-laplace}
r(z)
\;=\;
\int_0^\infty e^{-\lambda z}\,
\{J {}_\lambda J\}\, d\lambda
\;=\;
\int_0^\infty k\, e^{-\lambda z}\, d\lambda
\;=\;
\frac{k}{z},
\end{equation}
where the integral converges formally and the result is the
classical $r$-matrix.  The full quantum $R$-matrix is
\begin{equation}\label{eq:rosetta-cs-R}
R(z) \;=\; \exp\!\bigl(k/z\bigr)
\;=\;
\sum_{n=0}^{\infty}\,
\frac{k^n}{n!\,z^n},
\end{equation}
a formal power series in $z^{-1}$.

\begin{theorem}[CS $R$-matrix from the bar complex;
\ClaimStatusProvedHere]
\label{thm:rosetta-cs-r-matrix}
\index{R-matrix!abelian CS}
The spectral $R$-matrix of the abelian Chern--Simons boundary
algebra with OPE~\eqref{eq:rosetta-cs-ope} satisfies:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $R(z) = \exp(k/z)$, computed as the Laplace transform of
  the constant $\lambda$-bracket $\{J {}_\lambda J\} = k$;
\item the Yang--Baxter equation
  $R_{12}(u)\,R_{13}(u+v)\,R_{23}(v) =
   R_{23}(v)\,R_{13}(u+v)\,R_{12}(u)$;
\item the classical limit $r(z) = k/z$ satisfies the classical
  Yang--Baxter equation
  $[r_{12}(u),\, r_{13}(u+v)] + [r_{12}(u),\, r_{23}(v)]
   + [r_{13}(u+v),\, r_{23}(v)] = 0$;
\item antisymmetry $r(-z) = -r_{21}(z) = -r(z)$.
\end{enumerate}
\end{theorem}

\begin{proof}
(i) The Laplace transform is
equation~\eqref{eq:rosetta-cs-laplace}; exponentiation gives
$R(z) = \exp(r(z)) = \exp(k/z)$.

(ii) For the one-dimensional (abelian) case, $R(z) = \exp(k/z)$
is a scalar.  The Yang--Baxter equation reads
\[
e^{k/u}\,e^{k/(u+v)}\,e^{k/v}
\;=\;
e^{k/v}\,e^{k/(u+v)}\,e^{k/u},
\]
which holds because scalar multiplication is commutative: both
sides equal $\exp\bigl(k/u + k/(u+v) + k/v\bigr)$.

(iii) The classical $r$-matrix $r(z) = k/z$ is scalar, so all
commutators $[r_{ij}(z), r_{kl}(w)]$ vanish.  The CYBE
$0 + 0 + 0 = 0$ is satisfied.

(iv) Antisymmetry: $r(-z) = k/(-z) = -k/z = -r(z)$.  Since the
abelian case has a single generator, $r_{21}(z) = r(z)$, giving
$r(-z) = -r_{21}(z)$.
\end{proof}

\begin{remark}[Connection to Volume~I's DK ladder]
\label{rem:rosetta-cs-dk}
\index{DK ladder!abelian CS}
The spectral $R$-matrix at the evaluation locus recovers the
Drinfeld--Kohno braiding from Volume~I's DK ladder (DK-0).
For a non-abelian gauge group~$G$ with Lie algebra~$\fg$, the
classical $r$-matrix becomes
$r(z) = k\,\Omega/z$,
where $\Omega = \sum_a J^a \otimes J_a$ is the quadratic Casimir.
At the evaluation locus (i.e., the fundamental representation),
this is $r(z) = k P / z$ with $P$ the permutation matrix, and
the quantum $R$-matrix $R(z) = \mathrm{id} + \hh\, r(z) + O(\hh^2)$
matches the Drinfeld $R$-matrix to first order.  The abelian
case is the $G = U(1)$ specialization, where $\Omega = 1$ and
$R(z) = \exp(k/z)$.
\end{remark}

\medskip
\noindent\textbf{The three-atom comparison.}\enspace
The abelian CS algebra is the third atom in the Rosetta Stone,
completing the trio Heisenberg--Kac--Moody--CS.  The following table
extends the Heisenberg vs.~$\widehat{\mathfrak{sl}}_2$ table to
include the CS column:

\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{l|c|c|c}
\textbf{Feature}
  & \textbf{Heisenberg $\cH_k$}
  & $\widehat{\mathfrak{sl}}_{2,k}$
  & \textbf{Abelian CS} \\
\hline
OPE poles
  & double only
  & simple $+$ double
  & simple only \\
$d_{\mathrm{bracket}}$
  & $= 0$
  & $\neq 0$
  & $\neq 0$ \\
$d_{\mathrm{curvature}}$ (genus $0$)
  & $\neq 0$
  & $\neq 0$
  & $= 0$ \\
$\lambda$-bracket
  & $k\lambda$
  & $f^{ab}{}_c J^c + k\kappa^{ab}\lambda$
  & $k$ \\
$m_3$
  & $0$
  & $0$ (Koszul)
  & $0$ (Koszul) \\
$R$-matrix
  & trivial
  & nontrivial
  & $\exp(k/z)$ \\
Swiss-cheese (genus $0$)
  & flat
  & curved-closed
  & flat \\
Operadic type
  & $\Einf$
  & $\Einf$
  & $\Eone$ \\
\end{tabular}
\end{center}

The Heisenberg algebra is pure curvature (double pole, no bracket).
The CS algebra is pure bracket (simple pole, no curvature at genus~$0$).
The Kac--Moody algebra has both.  Every chiral algebra is, in the
bar-complex sense, a mixture of these three atomic behaviors.

\begin{remark}[Operadic type and braiding]
\label{rem:rosetta-cs-operadic}
The abelian CS algebra carries $\Eone$ structure (not $\Einf$)
because the simple-pole OPE is \emph{non-commutative} in the
spectral parameter: the ordering of line operators along the
topological direction~$\bR$ matters.  This is visible in the
$R$-matrix: $R(z) = \exp(k/z) \neq 1$ for $k \neq 0$, so the
braiding is nontrivial.  The Heisenberg algebra, by contrast, has
trivial braiding ($R = 1$) because the double-pole OPE is symmetric
under exchange, giving $\Einf$ structure.  The passage from $\Einf$
to $\Eone$ is the bar-complex avatar of the passage from commutative
to braided tensor categories.
\end{remark}


% ================================================================
\section{\texorpdfstring{$\mathcal{W}$-algebras: Koszul duality meets derived constructions}{$\mathcal{W}$-algebras: Koszul duality meets derived constructions}}
\label{sec:frame-w-algebras}
% ================================================================

The $\mathcal{W}$-algebras arise from affine Kac--Moody algebras
via quantum Drinfeld--Sokolov reduction.  For the principal nilpotent
embedding $f_{\mathrm{prin}} \hookrightarrow \mathfrak{g}$, the DS
functor produces
\begin{equation}\label{eq:frame-ds-definition}
\mathcal{W}^k(\mathfrak{g})
= H^0_{\mathrm{DS}}(\widehat{\mathfrak{g}}_k, f_{\mathrm{prin}}).
\end{equation}
For $\mathfrak{g} = \mathfrak{sl}_2$, this is the Virasoro algebra
$\mathrm{Vir}_c$ with $c = 1 - 6(k+1)^2/(k+2)$.
For $\mathfrak{g} = \mathfrak{sl}_3$, the result is the
$\mathcal{W}_3$ algebra with generators $T(z)$ (weight~$2$) and
$W(z)$ (weight~$3$) and central charge $c = 2 - 24(k+2)^2/(k+3)$.

\medskip
\noindent\textbf{The composite field phenomenon.}
The $T$--$T$ OPE is the standard Virasoro OPE with poles of
order~$4$, $2$, $1$:
\[
T(z)\,T(w) \sim \frac{c/2}{(z-w)^4}
  + \frac{2T(w)}{(z-w)^2}
  + \frac{\partial T(w)}{z-w}\,.
\]
This is quadratic in the generators and compatible with the
PBW spectral sequence.  But the $T$--$W$ and $W$--$W$ OPEs
involve the \emph{composite field}
\begin{equation}\label{eq:frame-w3-composite}
\Lambda(z) = :\!T(z)T(z)\!: - \tfrac{3}{10}\partial^2 T(z),
\end{equation}
which appears in the $W$--$W$ OPE at the quartic pole
(Definition~\ref{def:w3-algebra}; Theorem~\ref{thm:w-w-ope-complete}
for the complete expansion):
\[
W(z)\,W(w) \sim \frac{c/3}{(z-w)^6}
  + \frac{2T(w)}{(z-w)^4}
  + \frac{\partial T(w)}{(z-w)^3}
  + \frac{\tfrac{3}{10}\partial^2 T(w)
    + \tfrac{16}{22+5c}\Lambda(w)}{(z-w)^2}
  + \cdots
\]
The quartic pole involves $\Lambda$, a normally-ordered product of
generators---not a new generator.  In the PBW filtration, $\Lambda$
has conformal weight~$4$ but PBW degree~$2$: it is a double Wick
contraction that crosses filtration levels.

\begin{remark}[PBW degeneration is not automatic]
\label{rem:frame-pbw-warning}
For affine Kac--Moody algebras, the PBW spectral sequence degenerates
at~$E_2$ because the OPE is quadratic: all singular terms in
$J^a(z)\,J^b(w)$ involve at most two generators.  For $\mathcal{W}_3$,
the composite field~$\Lambda$ means that the $W$--$W$ OPE contains
products of generators at higher filtration level.  The $E_2$
differentials are non-trivial, and the spectral sequence requires
a separate degeneration argument
(Theorem~\ref{thm:pbw-koszulness-criterion}).  The claim ``quadratic
OPE implies $E_2$ collapse'' is \emph{false} for $\mathcal{W}$-algebras.
\end{remark}

\medskip
\noindent\textbf{Koszul duality commutes with DS reduction.}
The central theorem for $\mathcal{W}$-algebras is that Drinfeld--Sokolov
reduction commutes with Koszul duality
(Theorem~\ref{thm:w-algebra-koszul-main}):
\begin{equation}\label{eq:frame-w-koszul}
\mathcal{W}^k(\mathfrak{g})^!
\;\simeq\;
\mathcal{W}^{k'}(\mathfrak{g}),
\qquad
k' = -k - 2h^\vee.
\end{equation}
The Feigin--Frenkel involution $k \leftrightarrow -k - 2h^\vee$,
which we saw for Kac--Moody algebras in
\S\ref{sec:frame-nonabelian-preview}, descends through DS reduction
to the full $\mathcal{W}$-algebra tower.  For the Virasoro algebra
($\mathfrak{g} = \mathfrak{sl}_2$, $h^\vee = 2$), the dual levels
satisfy
\begin{equation}\label{eq:frame-virasoro-dual-central-charge}
c(k) + c(k') = 26.
\end{equation}
The number $26$ is the critical dimension of the bosonic string:
the combined central charge of the Virasoro algebra and its Koszul
dual equals the dimension at which the conformal anomaly cancels.
For $\mathcal{W}_3$ ($\mathfrak{g} = \mathfrak{sl}_3$,
$h^\vee = 3$):
\begin{equation}\label{eq:frame-w3-dual-central-charge}
c(k) + c(k') = 2(N{-}1)(2N^2{+}2N{+}1)\big|_{N=3} = 100.
\end{equation}

The proof of~\eqref{eq:frame-w-koszul} proceeds in two steps.
First, the DS functor is realized as a derived tensor product:
$\mathcal{W}^k(\mathfrak{g}) = \widehat{\mathfrak{g}}_k
\overset{L}{\otimes}_{\widehat{\mathfrak{n}}_+} \mathbb{C}_\chi$.
Second, the bar complex of this derived tensor product is compared
with the bar complex of $\widehat{\mathfrak{g}}_k$ restricted to
the BRST cohomology.  The BRST differential and the
bar differential commute at the chain level, so the DS reduction
can be performed inside the bar complex.  The Koszul dual then
inherits the level shift from the Kac--Moody duality.

\begin{center}
\small
\begin{tabular}{c|c|c|c}
& \textbf{Kac--Moody}
  $\widehat{\mathfrak{g}}_k$ &
\textbf{Virasoro}
  $\mathrm{Vir}_c$ &
$\mathcal{W}_3$ \\
\hline
Generators & $\{J^a\}$ (weight~1)
  & $T$ (weight~2)
  & $T, W$ (weights~2, 3) \\
Composite fields & None
  & None
  & $\Lambda = :\!TT\!: - \tfrac{3}{10}\partial^2 T$ \\
Max OPE pole & $2$ & $4$ & $6$ \\
PBW collapse & $E_2$ (automatic)
  & $E_2$ (automatic)
  & $E_2$ (separate argument) \\
Koszul dual & $\widehat{\mathfrak{g}}_{k'}$
  & $\mathrm{Vir}_{c'}$
  & $\mathcal{W}_3^{k'}$ \\
$c + c'$ & $2\dim(\mathfrak{g})$ & $26$ & $100$
\end{tabular}
\end{center}

The $\mathcal{W}$-algebra example demonstrates that chiral Koszul
duality is compatible with the fundamental derived operations of
conformal field theory.  Drinfeld--Sokolov reduction, which constructs
$\mathcal{W}$-algebras from Kac--Moody algebras as BRST cohomology,
is a derived functor in the sense of homological algebra; the fact
that it commutes with the bar construction means that the entire
Koszul duality machine descends through this derivation.  The
composite field phenomenon, far from obstructing the theory,
enriches it: the PBW spectral sequence acquires non-trivial higher
differentials that encode the normal-ordering structure of conformal
field theory.

% ================================================================
\section{\texorpdfstring{The braided world: lattice algebras and Yangians}{The braided world: lattice algebras and Yangians}}
\label{sec:frame-yangian-preview}
% ================================================================

Every chiral algebra considered so far --- Heisenberg, free fermions,
Kac--Moody, $\mathcal{W}$-algebras --- is $\Einf$-chiral:
its operations are commutative and local, configuration spaces
$C_n(X)$ are unordered, and Verdier duality on $\overline{C}_n(X)$
exchanges bar and cobar.  We now pass to chiral algebras with
$\Eone$-monoidal structure, where the operations are associative
but \emph{not} commutative.  This change of algebraic type, internal
to chiral geometry on a fixed curve, opens the door to quantum groups.

\medskip
\noindent\textbf{Lattice vertex algebras.}
Let $\Lambda$ be an even lattice with bilinear form
$\langle -,- \rangle$ and cocycle $\varepsilon \colon \Lambda \times
\Lambda \to \{\pm 1\}$.  The lattice vertex algebra
$V_\Lambda^\varepsilon$ is built from a Heisenberg sector (one current
$\alpha^i(z)$ per basis vector of $\Lambda \otimes \mathbb{C}$,
with double-pole OPE) together with vertex operators
$e^\alpha(z)$ for each $\alpha \in \Lambda$, satisfying
\[
e^\alpha(z)\,e^\beta(w) = \varepsilon(\alpha,\beta)\,
(z-w)^{\langle\alpha,\beta\rangle}\, e^{\alpha+\beta}(w)
+ \cdots
\]
The cocycle $\varepsilon$ controls the braiding.  When $\varepsilon$
is symmetric ($\varepsilon(\alpha,\beta) = \varepsilon(\beta,\alpha)$),
$V_\Lambda^\varepsilon$ is $\Einf$-chiral.  When $\varepsilon$ is
\emph{antisymmetric}
($\varepsilon(\alpha,\beta)\varepsilon(\beta,\alpha) = (-1)^{\langle\alpha,\beta\rangle}$),
the algebra acquires $\Eone$-monoidal structure: the bar complex uses
ordered configuration spaces $\overline{C}_n^{\mathrm{ord}}(X)$, and
the coproduct is no longer cocommutative.

Cocycle deformations at roots of unity produce quantum lattice
algebras $V_\Lambda^{N,q}$ for $N \geq 3$ and an antisymmetric
bilinear form~$q$ (Definition~\ref{def:lattice:cocycle-deformation}).
The $\Eone$ bar-cobar adjunction inverts the cocycle:
\begin{equation}\label{eq:frame-e1-inversion}
\barB^{\Eone}(V_\Lambda^{N,q})^!
\;\simeq\;
V_\Lambda^{N,-q},
\qquad
\text{i.e.,}\quad
\varepsilon \;\mapsto\; \varepsilon^{-1}.
\end{equation}
This is the $\Eone$ inversion principle
(Theorem~\ref{thm:e1-inversion-principle}): Koszul duality inverts
the braiding parameter.  The lattice structure provides a decisive
advantage: $V_\Lambda^\varepsilon$ decomposes into sectors indexed
by $\gamma \in \Lambda$, each finite-dimensional in fixed conformal
weight.  This \emph{sectorwise finiteness} bypasses the
thick-generation problems that plague the Yangian approach, yielding
unconditional factorization Drinfeld--Kohno equivalences at level~$1$
for simply-laced root systems
(Corollary~\ref{cor:lattice:factorization-dk-level1}).

\medskip
\noindent\textbf{Yangians.}
The Yangian $Y(\mathfrak{g})$ is $\Eone$-chiral: its operations are
associative but not commutative.  Configuration spaces are
ordered: $\overline{C}_n^{\mathrm{ord}}(X)$ replaces
$\overline{C}_n(X)$.  The bar complex uses ordered tuples, and
the coproduct is not cocommutative.

\begin{center}
\small
\begin{tabular}{c|c|c}
& \textbf{Heisenberg}
  ($E_\infty$-chiral) &
\textbf{Yangian} $Y(\mathfrak{g})$
  ($E_1$-chiral) \\
\hline
Configuration space & $C_n(X)$ (unordered)
  & $C_n^{\mathrm{ord}}(X)$ (ordered) \\
Coproduct & Cocommutative
  & Coassociative (not cocommutative) \\
Koszul dual & $\mathrm{Sym}^{\mathrm{ch}}(V^*)$
  & $Y_{R^{-1}}(\mathfrak{g})$ \\
Duality type & Lie $\leftrightarrow$ Com
  & $R \leftrightarrow R^{-1}$ \\
Self-dual? & No & Yes (classically)
\end{tabular}
\end{center}

The Yangian $Y(\mathfrak{g})$ is presented by the RTT relations,
which are quadratic in the $E_1$-chiral sense.  The quadratic
dual relations are the RTT relations with the inverse $R$-matrix
$R^{-1}(u)$ replacing~$R(u)$
(Theorem~\ref{thm:yangian-koszul-dual}).  At the classical limit
$\hbar = 0$, $R^{-1} = R$ and the Yangian is self-dual
(Corollary~\ref{cor:yangian-classical-self-dual}); at $\hbar \neq 0$,
the duality is a non-trivial involution.

The chain-level derived Drinfeld--Kohno theorem
(Theorems~\ref{thm:derived-dk-affine}
and~\ref{thm:derived-dk-yangian}) proves at the chain level:
\begin{equation}\label{eq:frame-derived-dk}
D^b(\mathrm{Rep}_{\mathrm{fd}}(Y_\hbar(\mathfrak{g})))
\;\simeq\;
D^b(\mathrm{Rep}_{\mathrm{fd}}(Y_{-\hbar}(\mathfrak{g})))
\end{equation}
with braiding reversal $R \mapsto R^{-1}$.  Under the Kazhdan
equivalence, this becomes $q \mapsto q^{-1}$ on quantum group
representations.  The factorization-level statement is proved on
the evaluation locus (Theorem~\ref{thm:factorization-dk-eval});
the extension to all finite-dimensional representations in type~$A$
is proved (Theorem~\ref{thm:dk-fd-typeA}); the full
category-$\mathcal{O}$ extension
$\mathrm{Fact}_{E_1}(Y(\mathfrak{g}))
\simeq \mathrm{Fact}_{E_1}(U_q(\mathfrak{g}))^{\mathrm{op}}$
remains conjectural (Conjecture~\ref{conj:derived-drinfeld-kohno}).

The passage from $\Einf$-chiral (Heisenberg) to $\Eone$-chiral
(Yangian) is an internal change of algebraic type within chiral
geometry on a fixed curve: from commutative/local factorization on
unordered configuration spaces to associative/nonlocal factorization on
ordered configuration spaces.  It is not the passage from curves to
higher-dimensional manifolds.  A separate topological ladder is
governed by little-disks $E_n$-algebras on real $n$-manifolds; for a
complex curve the relevant topological index is $n = 2$, not $n = 1$.
Chapter~\ref{ch:en-koszul-duality} develops that distinct topological
framework.

% ================================================================
\section{The main theorems}
\label{sec:frame-programme}
% ================================================================

The Heisenberg algebra has been our atom: the simplest chiral algebra
in which every construction of the monograph is visible by direct
calculation.  Bar complex, Koszul dual, inversion, curvature, genus
tower, complementarity, and factorization Drinfeld--Kohno have each
appeared here not as abstract consequences of general machinery but
as explicit geometric acts --- collision residues, Arnold
cancellations, clutching along nodal degenerations, Verdier duality
on configuration spaces.  The point of this atom is not merely
pedagogy.  It is that the general theorems are shadows of a single
geometric mechanism whose full visibility requires only one free
boson.  Every later chapter refines, deforms, and extends this
mechanism into nonabelian, nonlinear, and modular territory.

Across these examples, we have seen the core phenomena of the
monograph:
\begin{enumerate}
\item The bar complex from configuration space integrals,
  with $\dzero^{\,2} = 0$ forced by the Arnold relation
  (\S\ref{sec:frame-bar-deg2}).

\item The Koszul dual read from bar complex cohomology:
  $\mathcal{H}_k^! = \mathrm{Sym}^{\mathrm{ch}}(V^*)$,
  $\mathcal{F}^! = \beta\gamma$,
  $\widehat{\mathfrak{g}}_k^! = \widehat{\mathfrak{g}}_{-k-2h^\vee}$,
  $\mathcal{W}^k(\mathfrak{g})^! = \mathcal{W}^{-k-2h^\vee}(\mathfrak{g})$
  (\S\ref{sec:frame-koszul-dual},
   \S\ref{sec:frame-free-fields},
   \S\ref{sec:frame-nonabelian-preview},
   \S\ref{sec:frame-w-algebras}).

\item Bar-cobar inversion on the Koszul locus
  (\S\ref{sec:frame-inversion}).

\item Curvature at genus~$1$: $\dfib^{\,2} = \kappa \cdot \omega_1$,
  the passage to the coderived category
  (\S\ref{sec:frame-genus1}).

\item The genus tower with $\hat{A}$-genus generating function
  (\S\ref{sec:frame-genus-tower}).

\item Complementarity of quantum corrections
  (\S\ref{sec:frame-complementarity}).

\item The Lie--Com duality and the bracket/curvature decomposition
  (\S\ref{sec:frame-free-fields}).

\item The Borcherds identity and PBW spectral sequence
  (\S\ref{sec:frame-nonabelian-preview}).

\item DS-Koszul commutativity and composite fields
  (\S\ref{sec:frame-w-algebras}).

\item The $\Eone$ inversion principle and factorization DK
  (\S\ref{sec:frame-yangian-preview}).
\end{enumerate}

These instantiate the main theorems of the monograph:

\begin{itemize}
\item \textbf{Theorem~A}
  (Theorem~\ref{thm:bar-cobar-isomorphism-main};
  for the $\mathrm{A}_0/\mathrm{A}_1/\mathrm{A}_2$ decomposition
  see Remark~\ref{rem:theorem-A-decomposition}):
  \emph{Geometric bar-cobar duality.}
  What we saw as ``the bar complex produces a commutative Koszul
  dual'' generalizes to: the bar construction $\bar{B}(\cA)$ on an augmented chiral
  algebra \emph{is} the Koszul dual coalgebra---a dg factorization
  coalgebra on $\mathrm{Ran}(X)$, intertwined with Verdier duality
  and defined functorially over $\overline{\mathcal{M}}_{g,n}$.
  On the Koszul locus, $H^*(\bar{B}(\cA))$ is concentrated
  and equals the Koszul dual \emph{coalgebra}; the bar construction
  is its derived enhancement (off this locus, bar cohomology is
  not concentrated and there is no classical Koszul dual).  The Koszul dual \emph{algebra}~$\cA^!$ is obtained
  from this coalgebra by Verdier duality
  (Theorem~\ref{thm:bar-cobar-isomorphism-main}).  The cobar
  of the bar recovers~$\cA$ itself, not~$\cA^!$:
  $\Omega(\bar{B}(\cA)) \xrightarrow{\sim} \cA$ on the Koszul locus.
  The convolution Lie algebra
  $\mathrm{Hom}(\bar{B}(\cA), \cA)$
  (Convention~\ref{conv:bar-coalgebra-identity})
  mediates the adjunction: its Maurer--Cartan elements are the
  twisting morphisms, and the canonical MC element is the
  bar-cobar counit.

\item \textbf{Theorem~B}
  (Theorem~\ref{thm:higher-genus-inversion}):
  \emph{Bar-cobar inversion.}
  What we saw as ``cobar recovers Heisenberg'' generalizes to:
  on the Koszul locus (where the PBW spectral sequence collapses),
  the counit $\Omega \bar{B}(\mathcal{A}) \to \mathcal{A}$ is a
  quasi-isomorphism.  Off this locus, the counit persists as a
  curved quasi-isomorphism in the coderived category.

\item \textbf{Theorem~C}
  (Theorem~\ref{thm:quantum-complementarity-main}):
  \emph{Deformation-obstruction complementarity.}
  What we saw as ``deformation of $\mathcal{H}_k$ and obstruction
  of $\mathrm{Sym}^{\mathrm{ch}}(V^*)$ are complementary''
  generalizes to: for any Koszul pair $(\mathcal{A},
  \mathcal{A}^!)$, the deformation and obstruction spaces embed
  as complementary Lagrangians in a shifted-symplectic ambient
  space on $\overline{\mathcal{M}}_g$.
\end{itemize}

\subsection{The modular Koszul package}

The Heisenberg atom already contains the modular story in compressed
form: curvature at genus~$1$, the $\hat{A}$-genus generating function,
and complementarity of deformations and obstructions are all visible
by direct calculation.  The general theorems do not \emph{add} modular
structure to the genus-$0$ engine; they \emph{unfold} what was already
present in the bar complex's interaction with the clutching morphisms
of $\overline{\mathcal{M}}_{g,n}$.  The \emph{modular Koszul package}
articulates five target theorems:

\begin{enumerate}
\item[$A_{\mathrm{mod}}$.]
  \emph{Verdier-intertwined bar-cobar, functorial over
  $\overline{\mathcal{M}}_{g,n}$.}
  The bar-cobar adjunction extends to a modular operad map,
  with Verdier duality exchanging bar and cobar at every genus.

\item[$B_{\mathrm{mod}}$.]
  \emph{Inversion on the Koszul locus, coderived persistence off it.}
  The bar-cobar quasi-isomorphism holds on the Koszul locus at
  every genus; off this locus, the bar complex is curved and lives
  in the coderived category.

\item[$C_{\mathrm{mod}}$.]
  \emph{$(-1)$-shifted symplectic complementarity.}
  The deformation and obstruction spaces for a Koszul pair form
  complementary Lagrangians in a $(-1)$-shifted symplectic
  structure on $R\Gamma(\overline{\mathcal{M}}_g,
  \mathcal{Z}_{\mathcal{A}})$.

\item[\textbf{Index}.]
  \emph{Grothendieck--Riemann--Roch for modular deformations.}
  The genus series $\sum_g F_g x^{2g}$ is the $\hat{A}$-class
  pushforward of the universal Maurer--Cartan class along the
  family $\overline{\mathcal{M}}_{g,\bullet} \to \mathrm{pt}$.

\item[\textbf{DK}.]
  \emph{Derived Drinfeld--Kohno \textup{(}through DK-2/3,
  finite-dimensional type~$A$\textup{)}.}
  The $E_1$-factorization homology of the Yangian $Y(\mathfrak{sl}_N)$
  recovers the quantum group $U_q(\mathfrak{sl}_N)$ via a braided
  monoidal equivalence of finite-dimensional factorization categories.
\end{enumerate}

Theorems~A--C are proved in this monograph
(Chapters~\ref{chap:bar-cobar}--\ref{chap:higher-genus}).
The Index theorem is proved (Theorem~\ref{thm:family-index});
chain-level derived Drinfeld--Kohno is proved, and the
factorization statement is proved on the evaluation locus
(Theorem~\ref{thm:derived-dk-yangian};
Theorem~\ref{thm:factorization-dk-eval}), with the full
factorization statement conjectured.
The full formulation appears in
\S\ref{sec:modular-koszul-programme}.

\subsection{The operadic architecture}
\label{subsec:frame-operadic-architecture}

The genus tower of \S\ref{sec:frame-genus-tower} is organized by an
operadic structure that we now make visible in the Heisenberg example.

\subsubsection*{Genus $0$: $\mathrm{HyCom} \leftrightarrow \mathrm{Grav}$}

The Arnold relation (Proposition~\ref{prop:frame-arnold}) is the
defining relation of the \emph{gravity operad} $\mathrm{Grav}$,
which governs the genus-$0$ bar complex.  Its Koszul dual is the
\emph{hypercommutative operad} $\mathrm{HyCom}$, which governs the
cobar complex.  The genus-$0$ bar-cobar adjunction
\[
\bar{B} \colon \mathsf{Alg}_{\mathrm{HyCom}}
\rightleftarrows
\mathsf{coAlg}_{\mathrm{Grav}} :\! \Omega
\]
is an instance of operadic Koszul duality (Getzler--Kapranov~\cite{GK94}).
For Heisenberg:
\begin{itemize}
\item $\mathcal{H}_k$ is a $\mathrm{HyCom}$-algebra (the chiral
  operations are commutative and local).
\item $\bar{B}(\mathcal{H}_k)$ is a $\mathrm{Grav}$-coalgebra
  (the bar differential is controlled by the Arnold relation).
\item The cobar $\Omega\bar{B}(\mathcal{H}_k) \simeq \mathcal{H}_k$
  recovers the original algebra
  (\S\ref{sec:frame-inversion}).
\end{itemize}

The two operads are dual incarnations of a single structure:
$\mathrm{HyCom}(n) = H^*(\overline{M}_{0,n+1})$ (cohomology of
genus-$0$ moduli), and $\mathrm{Grav}(n) = H^*(\overline{M}_{0,n+1})^!$
(Koszul dual grading).  The genus-$0$ bar complex \emph{is} the
$\mathrm{Grav}$-coalgebra structure, and the collision differential
$\dzero^{\,2} = 0$
follows from the $\mathrm{Grav}$ relations (= Arnold).

\subsubsection*{Genus $1$: the elliptic operad}

At genus~$1$, the moduli space $\overline{\mathcal{M}}_{1,n}$
enters.  The bar complex on an elliptic curve acquires fiberwise
curvature $\dfib^{\,2} = k \cdot \omega_1$
(\S\ref{sec:frame-genus1}).  Operadically,
the genus-$1$ structure is governed by the \emph{elliptic operad}:
the collection $\{H^*(\overline{\mathcal{M}}_{1,n})\}_{n \geq 1}$
with composition maps from clutching morphisms.

For Heisenberg, the elliptic operad acts as follows.  The
$E_2$ non-holomorphicity (\S\ref{sec:frame-holomorphic-anomaly})
is the genus-$1$ modular completion of the genus-$0$ Arnold
relation: the Eisenstein series $E_2(\tau)$ fails to be modular
because the ``boundary of boundary'' at genus~$1$
acquires the nodal contribution $\delta_0 \in
\partial\overline{\mathcal{M}}_{1,1}$.  This is the clutching
morphism $\overline{\mathcal{M}}_{0,3} \to
\partial\overline{\mathcal{M}}_{1,1}$ that glues a genus-$0$
curve to itself.

\subsubsection*{All genera: the modular operad and clutching}

The full genus tower is organized by the \emph{modular operad}
$\{\overline{\mathcal{M}}_{g,n}\}_{2g-2+n>0}$
(Getzler--Kapranov~\cite{GeK98}).  A modular operad has two types of
composition:
\begin{enumerate}
\item \emph{Tree-level composition} ($\circ_i$): gluing marked
  points on different curves. This is the genus-$0$ operadic
  structure.
\item \emph{Self-gluing} ($\xi_{ij}$): identifying two marked
  points on the \emph{same} curve, increasing genus by~$1$.
  The clutching morphism
  $\xi \colon \overline{\mathcal{M}}_{g,n+2}
  \to \overline{\mathcal{M}}_{g+1,n}$
  glues marked points $i$ and $j$.
\end{enumerate}

For Heisenberg, self-gluing is the mechanism that produces the
genus tower:
\begin{itemize}
\item At genus~$0$: tree-level composition gives $\dzero^{\,2} = 0$
  (Arnold).
\item At genus~$1$: self-gluing of a genus-$0$ curve introduces
  $\dfib^{\,2} = k \cdot \omega_1$ (curvature from the new cycle).
\item At genus~$g$: iterated self-gluing produces
  $\mathrm{obs}_g = k \cdot \lambda_g$, with $\lambda_g$ emerging
  from $g$ independent cycles on the nodal degeneration.
\end{itemize}

The \emph{Feynman transform} of a modular operad (Getzler--Kapranov~\cite{GeK98})
provides the all-genus bar construction.  For the modular operad
$\overline{\mathcal{M}}$, the Feynman transform produces a twisted
modular operad whose algebras are precisely curved
$A_\infty$-algebras with the curvature controlled by the
self-gluing maps.  This is why the universal Maurer--Cartan class
$\Theta_{\mathcal{A}}$ of Definition~\ref{def:frame-modular-package}
lives in $\mathrm{Def}_{\mathrm{cyc}}(\mathcal{A})
\,\widehat{\otimes}\, R\Gamma(\overline{\mathcal{M}}_{g,\bullet},
\mathbb{Q})$: the cyclic deformations of $\mathcal{A}$ are coupled
to the cohomology of moduli by the Feynman transform, and the
genus-$g$ component of $\Theta_{\mathcal{A}}$ encodes how the
self-gluing maps act on the bar-complex curvature.

\subsection{The panorama}

This chapter has traced a single construction --- the geometric bar
complex from configuration space integrals --- through six families
of chiral algebras, revealing a different structural layer at each
stage:

\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{l|l}
\textbf{Example} & \textbf{Structural feature revealed} \\
\hline
Heisenberg $\mathcal{H}_k$
  & Arnold relation, bar-cobar inversion, genus tower,
    $\hat{A}$-genus \\
Free fermion / $\beta\gamma$
  & Lie--Com duality, acyclicity, three dualities distinguished \\
$\widehat{\mathfrak{sl}}_2$
  & Borcherds identity, PBW spectral sequence,
    Feigin--Frenkel involution \\
$\mathcal{W}_3$
  & Composite fields, higher OPE poles,
    DS-Koszul commutativity \\
Lattice $V_\Lambda^\varepsilon$
  & $\Eone$-monoidal structure, $\varepsilon \mapsto \varepsilon^{-1}$
    inversion, sectorwise finiteness \\
Yangian $Y(\mathfrak{g})$
  & $R \leftrightarrow R^{-1}$,
    derived Drinfeld--Kohno,
    quantum groups from factorization
\end{tabular}
\end{center}

The four irreducible geometric inputs --- the Arnold relation (genus~$0$
collision), Verdier duality (Ran-space self-duality), genus-$1$ curvature
($\dfib^{\,2} = \kappa \cdot \omega_1$), and clutching (modular operad
structure) --- are the seeds from which the entire theory grows.  The
progression from Heisenberg to Yangians is not a sequence of
complications but a sequence of \emph{enrichments}: each example
activates a new piece of the chiral Koszul duality machine while
preserving everything already established.

The remainder of this monograph develops these constructions in full
generality (Part~I), carries them out for every major family
(Part~II), and connects them to BV-BRST quantization, Feynman
integrals, and holomorphic-topological field theory (Part~III).
