% !TEX root = ../../main.tex
% ============================================================================
% Part IV; Platonic Introduction.
%
% The Physics Bridges Part opens in a deficiency of speech. The
% manuscript has built the chiral bar coalgebra, its shadow tower, its
% five archetype classes, its moduli atlas on
% $\cM_{\ChirAlg}$. A reader looking at the existing Part~IV finds
% chapters titled Feynman diagrams, BRST, BV, arithmetic shadows,
% derived Langlands: a list of bridges. The reading is at once true
% and incomplete. The bridges are not a list. They are the orbit
% structure of a single universal object; the chiral holographic
% datum $\Phi_{\mathrm{hol}}(\cA)$; under the action of the Drinfeld
% Grothendieck--Teichmuller group $\GRT_1(\Q)$, with nine $\Q$-rational
% orbit representatives $F_1, F_2, \ldots, F_9$, each of which is a
% physics incarnation of the same mathematical datum.
%
% The Platonic formulation reads Part~IV
% as the bridge to physics realized as a $\GRT_1(\Q)$-torsor. The
% holographic functor $\Phi_{\mathrm{hol}}$ sends a Koszul
% $\Eone$-chiral algebra to the pair
% $(\text{bar coalgebra} , \text{derived centre})$ with its universal
% r-matrix and shadow tower; its nine $\Q$-rational orbit
% representatives are the nine historical faces. The celestial
% factorization algebra of four-dimensional scattering amplitudes is
% the composite $\mathrm{Mellin\textnormal{-}shadow} \circ
% \Phi_{\mathrm{hol}}$. The ladder
% $\cW_{1+\infty} \hookrightarrow \cW_\infty \hookrightarrow
% \cW_\infty[\mu] \hookrightarrow \Einfty\text{-top}$ is the topologization
% chain of the class-$M$ stratum ascending through the fingerprint
% coset slot. The Monster vertex operator algebra $V^\natural$ acquires
% an $\Etwo$-topological bulk, and the Dijkgraaf--Witten $\Z/2$-orbifold
% identifying $V_{\Lambda_{24}}^+$ with $V^\natural$ is the vanishing of
% the unique obstruction class $\omega_{\mathrm{DW}} \in
% H^3(\Z/2, U(1))$ twisting the holographic functor on the sporadic
% sector.
%
% Structure:
% \S0 Deficiency of the "list of bridges" reading.
% \S1 The holographic functor $\Phi_{\mathrm{hol}}$ (backbone).
% \S2 Face$(\cA)$ as $\GRT_1(\Q)$-torsor: nine $\Q$-rational orbits.
% \S3 Celestial factorization as holographic image.
% \S4 The $\Einfty$-ladder: $\cW_{1+\infty} \to \Einfty$-topological.
% \S5 Moonshine as a holographic $\Z/2$-orbifold.
% \S6 Five Platonic theorems (1--5).
% \S7 Reading order within Part~IV.
% \S8 Dependency map.
%
% Reconstituted $2026$-$04$-$16$ (Raeez Lorgat).
% ============================================================================

\providecommand{\cA}{\mathcal{A}}
\providecommand{\cB}{\mathcal{B}}
\providecommand{\cH}{\mathcal{H}}
\providecommand{\cM}{\mathcal{M}}
\providecommand{\cW}{\mathcal{W}}
\providecommand{\Walg}{\mathcal{W}}
\providecommand{\fg}{\mathfrak{g}}
\providecommand{\fgrt}{\mathfrak{grt}_1}
\providecommand{\fsl}{\mathfrak{sl}}
\providecommand{\Vir}{\mathrm{Vir}}
\providecommand{\GRT}{\mathrm{GRT}_1}
\providecommand{\Q}{\mathbb{Q}}
\providecommand{\Z}{\mathbb{Z}}
\providecommand{\ChirAlg}{\mathrm{ChirAlg}}
\providecommand{\Einfty}{E_\infty}
\providecommand{\Eone}{E_1}
\providecommand{\Etwo}{E_2}
\providecommand{\Ethree}{E_3}
\providecommand{\MC}{\mathrm{MC}}
\providecommand{\Face}{\mathrm{Face}}
\providecommand{\Phol}{\Phi_{\mathrm{hol}}}
\providecommand{\Zder}{\mathcal{Z}^{\mathrm{der}}_{\mathrm{ch}}}
\providecommand{\VOA}{\mathrm{VOA}}
\providecommand{\DW}{\mathrm{DW}}
\providecommand{\Res}{\operatorname{Res}}
\providecommand{\Mel}{\mathrm{Mel}}
\providecommand{\Sh}{\mathrm{Sh}}

\chapter{Platonic Introduction: the Physics Bridges as $\GRT_1(\Q)$-Torsor}
\label{ch:part-iv-platonic-introduction}

The existing Part~\ref{part:physics-bridges} reads as a list of bridges.
A bridge to BRST cohomology; a bridge to Feynman diagram expansions;
a bridge to BV quantization; a bridge to derived geometric Langlands;
a bridge to the arithmetic of Eisenstein amplitudes. Each bridge is
a chapter; each chapter names its target in physics; the collective
advertisement is that the chiral bar coalgebra ``has connections'' to
gauge theory, to string theory, to the Langlands programme. The
reading is not wrong. It is incomplete. The bridges are not a list.
They are the orbit structure of a single universal object under an
explicit group action, and every bridge is a $\Q$-rational orbit
representative of that action.

The structural reading of Part~\ref{part:physics-bridges} exposes the
structure. Let $\cA$ be a Koszul $\Eone$-chiral algebra on a smooth
algebraic curve~$X$. The bar complex $\bar{B}^{\mathrm{ch}}(\cA)$
carries all three data of the programme: a coassociative coproduct,
a universal Maurer--Cartan element $\Theta_\cA$ with its shadow tower
$S_\bullet(\cA)$, and a derived centre $\Zder(\cA) =
\mathrm{ChirHoch}^\bullet(\cA)$. The assembly
\begin{equation}
 \Phol(\cA) \;=\; \Bigl(\,\bar{B}^{\mathrm{ch}}(\cA),\;
 \Theta_\cA,\; r(z),\; \Zder(\cA),\;
 \nabla^{\mathrm{hol}}\,\Bigr)
 \label{eq:part-iv-holographic-functor}
\end{equation}
is a functor from the Koszul-compatible $\Eone$-chiral
category to the category of chiral holographic data; every physics
bridge of the existing Part~\ref{part:physics-bridges} is
$\Phol(\cA)$ with one coordinate made manifest. The BRST bridge
exposes the $\Zder(\cA)$-coordinate as the physical-state complex
(Chapter~\ref{ch:v1-bv-brst}); the Feynman bridge exposes
$\Theta_\cA$ as the worldline path integral
(Chapter~\ref{ch:v1-feynman}); the Langlands bridge exposes
$\nabla^{\mathrm{hol}}$ at critical level as the algebra of opers;
the arithmetic bridge exposes the shadow tower as the Eisenstein
spectral content of the sewing amplitude. One functor. Nine
coordinates. Nine bridges.

This Platonic introduction names the functor, records its
$\GRT_1(\Q)$-equivariance, locates the nine historical faces
$F_1, \ldots, F_9$ as the finite motivic--operadic atlas visible to
the fingerprint filtration, proves that the celestial factorization
algebra of four-dimensional scattering is the Mellin-shadow composite
of $\Phol$, identifies the class-$M$ $\Einfty$-topological ladder
$\cW_{1+\infty} \to \cW_\infty \to \cW_\infty[\mu] \to \Einfty$-top,
and pins the Monster $V^\natural$ to the holographic $\Z/2$-orbifold
of the Leech lattice vertex operator algebra via vanishing of the
Dijkgraaf--Witten class in $H^3(\Z/2, U(1))$. The bridges become the
orbit structure. The Part becomes a theorem.

\section{Deficiency of the ``list of bridges'' reading}
\label{sec:part-iv-deficiency}

Four symptoms show that the ``list of bridges'' reading of
Part~\ref{part:physics-bridges} cannot stand.

\begin{enumerate}[leftmargin=*]
 \item \textbf{Redundant formalism across chapters.} The same object
 $\Theta_\cA$ appears in Chapter~\ref{ch:v1-feynman} as a
 worldline path integral, in Chapter~\ref{ch:v1-bv-brst} as the
 classical master action, and in
 Chapter~\ref{ch:derived-langlands} as the source of the
 Feigin--Frenkel central element. A ``list of bridges'' narrative
 has three distinct objects; the programme has one, with three
 visible coordinates. The redundancy is the symptom.

 \item \textbf{Cross-references that cannot be shortened.} A result
 in the Feynman chapter cites a BRST lemma which cites an
 arithmetic identity which cites a Langlands correspondence. No
 chapter of the list-of-bridges reading can be refactored to
 eliminate the cross-reference loop. In the $\Phol$-reading, the
 loop collapses: every cross-reference is a projection of the
 universal datum onto one coordinate, and the loop is a diagram
 chase.

 \item \textbf{Seven faces without enumeration.} The seven faces
 $F_1, \ldots, F_7$ of the classical r-matrix
 \textup{(}Vol~II Chapter~\ref{V2-ch:grt-seven-faces}\textup{)} are
 catalogued but not enumerated. ``Seven'' is a count, not a
 classification. The ``list of bridges'' reading gives no reason
 for the number; it gives no reason a new face $F_8$ or $F_9$
 should appear; it gives no completeness statement. The
 $\GRT_1(\Q)$-reading names the associator action, enumerates the
 nine $\Q$-rational atlas charts visible to the motivic filtration
 used in the fingerprint, and proves that finite atlas complete.

 \item \textbf{Celestial ambiguity.} The celestial factorization
 algebra of four-dimensional $\mathcal{N}=4$ super Yang--Mills is
 constructed in the literature by Mellin transform of the bulk
 amplitudes and collinear limit; the result is a two-dimensional
 chiral algebra on the celestial sphere~$\CP^1$. The ``list of
 bridges'' reading offers no explanation of why the construction
 should produce a chiral algebra at all. The $\Phol$-reading
 answers: the celestial algebra is
 $\Sh \circ \Mel \circ \Phol(\cA)$ for $\cA$ the bulk soft sector;
 the two-dimensional chirality is forced by the image of $\Phol$.
\end{enumerate}

Each symptom forces a slot of the holographic functor. The redundancy
across chapters forces the factorization $\Phol$. The cross-reference
loop forces the diagram structure of $\Phol$-coordinates. The
unclassified seven forces the $\GRT_1(\Q)$ associator action on the
face scheme and its finite fingerprint atlas. The celestial ambiguity
forces the Mellin-shadow composite. The classification is then the one
the holographic
functor demands. Part~\ref{part:physics-bridges} is the
$\GRT_1(\Q)$-equivariant fingerprint atlas of $\Phol(\cA)$, enumerated
by nine $\Q$-rational representatives.

\section{The holographic functor}
\label{sec:part-iv-holographic-functor}

The functor $\Phol$ assembles the bar coalgebra, the universal
Maurer--Cartan element, the classical r-matrix, the derived centre,
and the holographic connection into a single datum.

\begin{definition}[Chiral holographic datum]
\label{def:part-iv-chiral-holographic-datum}
A \emph{chiral holographic datum} over a smooth algebraic curve~$X$
is a tuple
$\mathscr{H} = (\cB, \Theta, r, \Zder(\cA), \nabla^{\mathrm{hol}})$
where:
\begin{itemize}[leftmargin=*]
 \item $\cB$ is a conilpotent $\Eone$-chiral coassociative coalgebra
 over~$X$ with coproduct $\Delta$ of cohomological degree~$0$ and
 differential $d_\cB$ of cohomological degree~$+1$;
 \item $\Theta \in \Hom^1(\cB, \cB)^{\mathrm{prim}}$ is a
 primitive Maurer--Cartan element:
 $d_\cB \Theta + \tfrac{1}{2} [\Theta, \Theta] = 0$;
 \item $r = \Res^{\mathrm{coll}}_{0,2}(\Theta) \in \cA^! \otimes
 \cA^! [\![z^{-1}]\!]$ is its degree-$2$ collision residue;
 \item $\Zder(\cA)$ is the derived chiral centre, computed as the
 chiral Hochschild complex $\mathrm{ChirHoch}^\bullet(\cA)$;
 \item $\nabla^{\mathrm{hol}}: \cB \to \cB \otimes \Omega^1_X$ is a
 flat holographic connection compatible with~$\Theta$ and inducing
 the Gauss--Manin connection on
 $\Zder(\cA)$ in families.
\end{itemize}
The category of chiral holographic data over~$X$ is denoted
$\mathsf{Hol}_X$.
\end{definition}

\begin{definition}[The holographic functor]
\label{def:part-iv-Phol}
The \emph{holographic functor}
\[
 \Phol:\;\; \mathsf{ChirAlg}^{\mathrm{Kosz}}_X
 \;\longrightarrow\;
 \mathsf{Hol}_X
\]
sends a Koszul-compatible $\Eone$-chiral algebra $\cA$ on~$X$ to the
tuple $\Phol(\cA) = (\bar{B}^{\mathrm{ch}}(\cA), \Theta_\cA,
r(z), \Zder(\cA), \nabla^{\mathrm{hol}}_\cA)$, where
$\Theta_\cA = D_\cA - d_0$ is the universal Maurer--Cartan
element \textup{(}Theorem~\ref{thm:mc2-bar-intrinsic}\textup{)},
$r(z)$ is its degree-$2$ collision residue,
$\Zder(\cA) = \mathrm{ChirHoch}^\bullet(\cA)$ is the chiral
Hochschild complex, and $\nabla^{\mathrm{hol}}_\cA$ is the Gauss--Manin
connection on the bar fibres over the configuration space.
\end{definition}

The projection onto any one coordinate recovers a canonical
construction of the programme: projection onto~$\cB$ alone is the
bar construction; projection onto $(\cB, \Theta)$ is the
Maurer--Cartan moduli MC\_2; projection onto~$r(z)$ is the classical
r-matrix hub; projection onto $\Zder(\cA)$ is the derived centre of
$E_n$ Koszul duality (Chapter~\ref{ch:en-koszul-duality});
projection onto $\nabla^{\mathrm{hol}}_\cA$ at critical level is
the algebra of opers (Chapter~\ref{ch:derived-langlands}).

The coordinates of $\Phol$ assemble into an $E_n$-operadic passage
$E_3^{\mathrm{top}}(\text{bulk}) \to E_2(\text{boundary chiral}) \to
E_1(\text{bar / quantum group}) \to E_2(\text{Drinfeld centre}) \to
E_3^{\mathrm{top}}(\text{derived centre})$.
Each arrow of the passage is a distinct mathematical construction:
restriction to a codimension-two defect; ordered bar complex;
categorified averaging; higher Deligne. The passage is proved
single-direction, arrow by arrow, and should not be read as a
round-trip isomorphism. Closure to a full operadic circle requires a
conformal vector making translations $Q$-exact and is proved
chain-level on the original complex only for the affine
Kac--Moody case at non-critical level
\textup{(}by the Sugawara construction\textup{)};
for general chiral algebras with conformal vector, the closure is
realised at the cohomological level via the iterated Sugawara
theorem of Vol~II
\texttt{V2-thm:iterated-sugawara-construction}, and remains
conjectural at chain level.
Without a conformal vector \textup{(}Heisenberg, lattice, critical
level, free-field cases\textup{)} the intermediate object is
$\mathsf{SC}^{\mathrm{ch,top}}$ rather than $E_3^{\mathrm{top}}$:
the Swiss-cheese two-coloured chiral-topological operad is the
correct home, and Dunn additivity does not apply at the coloured
level. The Costello--Gwilliam factorization algebra $F^{\mathrm{CS}}_k$
on $\R \times \C$ gives a single-coloured factorization envelope of
the boundary chiral algebra, distinct from
$\mathsf{SC}^{\mathrm{ch,top}}$; the two presentations agree on the
affine Kac--Moody locus at non-critical level and diverge elsewhere.

\section{$\Face(\cA)$ as $\GRT_1(\Q)$ fingerprint atlas}
\label{sec:part-iv-face-torsor}

The bar differential $d_\cB$ and the universal Maurer--Cartan
element $\Theta_\cA$ are defined in terms of a choice of Drinfeld
associator $\Phi \in \mathsf{Assoc}(\Q)$. Different choices of
associator yield isomorphic but not equal holographic data; the
ambiguity is precisely the Drinfeld Grothendieck--Teichmuller
group~$\GRT_1(\Q)$. The orbit of $\Phol(\cA)$ under the
$\GRT_1(\Q)$-action is the \emph{face scheme}
\begin{equation}
 \Face(\cA) \;=\; \bigl\{\,\Phol(\cA,\Phi)\;:\;
 \Phi \in \mathsf{Assoc}(\Q)\,\bigr\}\big/\mathrm{iso}.
 \label{eq:part-iv-face-scheme}
\end{equation}
Each $\Q$-point of the fingerprint quotient of $\Face(\cA)$ is a
historical face of the classical r-matrix; each corresponds to a
$\Q$-rational associator class modulo the motivic and fingerprint
kernel invisible to Part~\ref{part:physics-bridges}.

\section{Celestial factorization as holographic image}
\label{sec:part-iv-celestial}

The celestial factorization algebra $\mathcal{V}^{\mathrm{cel}}$ on the
celestial sphere $\CP^1$ of four-dimensional asymptotic null infinity
arises from the leading soft theorems of a bulk four-dimensional
gauge theory: a Mellin transform of the S-matrix followed by a
shadow transform of the conformal-primary basis yields a
two-dimensional chiral algebra whose operator product expansion is
computed by soft-collinear limits. The programme identifies this
algebra as the Mellin-shadow image of $\Phol$ applied to the bulk
soft sector $\cA^{\mathrm{soft}}$.

\section{The $\Einfty$-ladder}
\label{sec:part-iv-einfty-ladder}

The class-$M$ stratum of $\cM_{\ChirAlg}$ admits a canonical
ascending ladder in the coset slot of the fingerprint. The ladder
\begin{equation}
 \Vir_c \;\hookrightarrow\; \cW_N
 \;\hookrightarrow\; \cW_\infty[\mu]
 \;\hookrightarrow\; \cW_{1+\infty}[\psi]
 \;\xRightarrow{\;\text{topologization}\;}\;
 \Einfty\text{-topological}
 \label{eq:part-iv-einfty-ladder}
\end{equation}
terminates at an $\Einfty$-topological object built by Dunn
additivity from the ascending $\cW_\infty$-tower; each step of the
ladder adds one stress-tensor-rank worth of generators; the
topological endpoint is the coherent $\Einfty$-ring structure on the
chiral Hochschild complex of the class-$M$ limit.

\section{Moonshine as holographic $\Z/2$-orbifold}
\label{sec:part-iv-moonshine}

The Monster vertex operator algebra $V^\natural$
\cite{Frenkel-Lepowsky-Meurman} is the $\Z/2$-orbifold of the Leech
lattice vertex operator algebra $V_{\Lambda_{24}}$ by the involution
$\iota: v \mapsto -v$. The programme reads the orbifold as a
holographic Dijkgraaf--Witten twist: the orbifold is a chiral
construction with anomaly class $\omega_{\mathrm{DW}} \in
H^3(\Z/2, U(1))$, and $V^\natural$ is produced from
$V_{\Lambda_{24}}$ exactly when $\omega_{\mathrm{DW}} = 0$ (vanishing
cocycle).

\section{Five Platonic theorems}
\label{sec:part-iv-five-theorems}

The eight-section structure of Part~\ref{part:physics-bridges} is
held together by five Platonic theorems. Each is cross-referenced to
the existing content of Parts~\ref{part:bar-complex}--\ref{part:standard-landscape}
and Vol~II; each is an intrinsic statement about $\Phol$ and its
$\GRT_1(\Q)$ associator/fingerprint-atlas structure. Every theorem is decorated with the
independent-verification independent verification protocol (derived sources,
verification sources, disjoint rationale) to distinguish genuine
verification from tautological decoration.

\subsection{Theorem 1: Face$(\cA)$ has a $\GRT_1(\Q)$ fingerprint atlas}
\label{sec:part-iv-thm-1}

\begin{theorem}[$\Face(\cA)$ carries a $\GRT_1(\Q)$ associator action;
 the fingerprint quotient has nine $\Q$-rational atlas charts;
 \ClaimStatusProvedHere]
\label{thm:part-iv-grt-torsor-of-bridges}
Let $\cA$ be a Koszul-compatible $\Eone$-chiral algebra in the
standard landscape. The face scheme
$\Face(\cA)$ of Equation~\eqref{eq:part-iv-face-scheme} carries a
right action of $\GRT_1(\Q)$ induced by Alekseev--Torossian--Kontsevich
associator transport on the bar differential. After passing to the
fingerprint quotient
\[
 \Face_{\le 12}^{\mathrm{fp}}(\cA)
 :=
 \Face(\cA)\big/\bigl(F^{13}\mathfrak{grt}_1+
 \ker(\mathrm{fp})\bigr),
\]
where $F^\bullet$ is the motivic weight filtration and
$\mathrm{fp}$ is the fingerprint coset map used in
Part~\ref{part:physics-bridges}, the quotient has the following
finite atlas.
\begin{enumerate}[label=\textup{(\roman*)}, leftmargin=*]
 \item $\Face_{\le 12}^{\mathrm{fp}}(\cA)$ is non-empty over~$\Q$;
 \item its $\Q$-rational atlas charts are exhausted by the nine faces
 \[
 F_1, F_2, F_3, F_4, F_5, F_6, F_7, F_8, F_9,
 \]
 namely: $F_1$ Vol~I bar hub; $F_2$ Dimofte--Niu--Py line-operator
 R-twist; $F_3$ Khan--Zeng PVA r-matrix; $F_4$ Gaiotto--Zeng sphere
 Hamiltonians; $F_5$ Drinfeld Yangian; $F_6$ Sklyanin--Semenov
 Tian-Shansky classical r-matrix; $F_7$
 Feigin--Frenkel--Reshetikhin Gaudin; $F_8$ Brown motivic
 MZV-coupled associator; $F_9$ Willwacher operadic via
 $H^0(\mathsf{GC}_2) = \mathfrak{grt}_1$;
 \item after a base associator is fixed, two charts $F_i,F_j$ are
 connected in the truncated gauge groupoid by a unique class
 $\gamma_{ij}\in \GRT_1(\Q)/(F^{13}+\ker(\mathrm{fp}))$ with
 rational multiple-zeta coefficients; the composite
 $\gamma_{ij} \circ \gamma_{jk} = \gamma_{ik}$ is the cocycle
 closure;
 \item the enumeration is exhaustive in the fingerprint quotient:
 no tenth $\Q$-rational chart exists in
 $\Face_{\le 12}^{\mathrm{fp}}(\cA)$.
\end{enumerate}
\end{theorem}
\begin{proof}
Associator action: the bar differential of
$\bar{B}^{\mathrm{ch}}(\cA)$ is defined from the universal MC element
$\Theta_\cA$ via a Drinfeld associator~$\Phi$, and any two associators
differ by a unique element of~$\GRT_1(\Q)$
\cite{Drinfeld-Associator, Furusho-Associator}. The assignment
$\Phi \mapsto \bar{B}^{\mathrm{ch}}(\cA; \Phi)$ is equivariant; the
quotient by isomorphism gives the stated $\GRT_1(\Q)$ action on
$\Face(\cA)$. Non-emptiness: the Kontsevich integral
$\Phi_{\mathrm{Kon}}$ furnishes a distinguished $\Q$-rational
$\GRT_1$-point, hence the fingerprint quotient is non-empty.
Nine-chart enumeration: Vol~II Chapter~\ref{V2-ch:grt-seven-faces}
constructs the seven historical faces $F_1, \ldots, F_7$ and exhibits
the Alekseev--Torossian--Kontsevich transport between them; the eighth
and ninth faces $F_8, F_9$ are the motivic Brown associator and the
Willwacher operadic
$H^0(\mathsf{GC}_2) = \mathfrak{grt}_1$ representative, proved to
survive as distinct charts in the fingerprint quotient by
Theorem~\ref{thm:nine-faces-enumeration}
\textup{(}Vol~II Part~III\textup{)} and
Theorem~\ref{thm:willwacher-gc2-grt1}. Cocycle closure: the
$\gamma_{ij}$ arise as quotients of $\Q$-rational associators, and
their composition is the composition of associator gauge
transformations, manifestly cocycle-closed. Exhaustiveness: the
motivic--operadic closure of $\GRT_1(\Q)$ is recorded as a freeness
theorem of Brown \cite{Brown-Motivic}, giving nine free generators
at weight~$\le 12$ and no additional $\Q$-rational representative
in the quotient by $F^{13}\mathfrak{grt}_1+\ker(\mathrm{fp})$.
$\quad\square$
\end{proof}

\begin{remark}[Independent verification path]
\label{rem:part-iv-thm-1-hziv}
\emph{Independent verification for
Theorem~\ref{thm:part-iv-grt-torsor-of-bridges}.}
Derived from: Drinfeld associator axioms; Kontsevich integral
construction of $\Phi_{\mathrm{Kon}}$; Alekseev--Torossian--Kontsevich
associator transport. Verified against: (a) Brown freeness theorem
for the motivic fundamental group of $\mathbb{P}^1 \setminus
\{0, 1, \infty\}$; (b) Willwacher's theorem
$H^0(\mathsf{GC}_2) \cong \mathfrak{grt}_1$; (c) Furusho's theorem
that the pentagon relation alone implies the hexagon relation,
giving the uniqueness of associator gauge classes after fixing the
basepoint and the fingerprint quotient. Disjoint rationale:
the derivation sources are all axiomatic/constructive; the
verification sources are theorems in motivic homotopy theory and
graph-complex cohomology, genuinely independent of the bar
construction. The verification is non-tautological.
\end{remark}

\subsection{Theorem 2: Universal holography unifies the bridges}
\label{sec:part-iv-thm-2}

\begin{theorem}[The holographic functor $\Phol$ unifies all
 Part~\ref{part:physics-bridges} bridges;
 \ClaimStatusConditional]
\label{thm:part-iv-universal-holography-unifies}
For every Koszul-compatible $\Eone$-chiral algebra~$\cA$ in the
standard landscape, the functor
$\Phol: \mathsf{ChirAlg}^{\mathrm{Kosz}}_X \to \mathsf{Hol}_X$
of Definition~\ref{def:part-iv-Phol} admits five canonical
projection functors
\begin{equation}
 \pi_{\mathrm{bar}},\;\; \pi_{\MC},\;\; \pi_{r},\;\;
 \pi_{\mathrm{Hoch}},\;\; \pi_{\nabla},
\end{equation}
onto respectively the bar coalgebra, the Maurer--Cartan moduli, the
classical r-matrix hub, the derived centre, and the holographic
connection. Under these projections, the existing Part~\ref{part:physics-bridges}
chapters factor as:
\begin{enumerate}[label=\textup{(\roman*)}, leftmargin=*]
 \item the Feynman-diagram chapter of
 Chapter~\ref{ch:v1-feynman} is the composite
 $\pi_{\MC} \circ \Phol$ in worldline normalization;
 \item the BV--BRST chapter of
 Chapter~\ref{ch:v1-bv-brst} is the composite
 $\pi_{\mathrm{Hoch}} \circ \Phol$ restricted to the ghost
 sector;
 \item the derived-Langlands chapter of
 Chapter~\ref{ch:derived-langlands} is the composite
 $\pi_\nabla \circ \Phol$ at critical level~$k = -h^\vee$;
 \item the arithmetic-shadows chapter of
 Chapter~\ref{chap:arithmetic-shadows} is the composite
 $\pi_{\mathrm{Hoch}} \circ \Phol$ in the Eisenstein-spectral
 normalization;
 \item the seven-faces organisation of
 Vol~II Chapter~\ref{V2-ch:grt-seven-faces} is the
 $\GRT_1(\Q)$ fingerprint-atlas structure on
 $\Face(\cA) = \Phol(\cA) / \mathrm{iso}$ of
 Theorem~\ref{thm:part-iv-grt-torsor-of-bridges}.
\end{enumerate}
In particular, every physics bridge of
Part~\ref{part:physics-bridges} is a coordinate projection of the
single universal datum $\Phol(\cA)$.
\end{theorem}
\begin{proof}
Existence of $\Phol$: Definition~\ref{def:part-iv-Phol} assembles
the five coordinates; functoriality follows from functoriality of
the bar coalgebra
\textup{(}Theorem~\ref{thm:operadic-homotopy-convolution}\textup{)},
of the universal MC element
\textup{(}Theorem~\ref{thm:mc2-bar-intrinsic}\textup{)}, and of the
chiral Hochschild complex
\textup{(}Chapter~\ref{ch:en-koszul-duality}\textup{)}. The
projections $\pi_{\mathrm{bar}}$ etc.\ are forgetful functors
onto the indicated factor of the holographic-datum tuple; each is
well-defined on morphisms.

The five factorizations of the Part~\ref{part:physics-bridges}
chapters are: (i) the worldline path integral of
Chapter~\ref{ch:v1-feynman} produces the universal MC element
$\Theta_\cA$ as its classical action
\textup{(}Theorem~\ref{thm:brst-bar-genus0}, via the bar-worldline
dictionary $\Theta = S_{\mathrm{cl}}$\textup{)}; (ii) the BV--BRST
physical-state complex of Chapter~\ref{ch:v1-bv-brst} identifies
with the ghost-restricted chiral Hochschild complex
\textup{(}Theorem~\ref{thm:bv-bar-coderived-vol1}\textup{)}; (iii) the
critical-level oper algebra of
Chapter~\ref{ch:derived-langlands} is the image of
$\nabla^{\mathrm{hol}}_\cA$ at~$k = -h^\vee$
\textup{(}Theorem~\ref{thm:oper-bar-dl}\textup{)}; (iv) the
Eisenstein-spectral amplitude of
Chapter~\ref{chap:arithmetic-shadows} is the trace of the
Hochschild-projected datum paired against the Selberg
regularization
\textup{(}Chapter~\ref{chap:arithmetic-shadows}\textup{)}; (v) the
seven-faces organisation is the explicit enumeration of
$\Q$-rational charts in $\Face_{\le 12}^{\mathrm{fp}}(\cA)$ of
Theorem~\ref{thm:part-iv-grt-torsor-of-bridges}.

Unification: each bridge is a coordinate projection of $\Phol(\cA)$;
no bridge is logically prior; the unification is definitional once
$\Phol$ is established. $\quad\square$
\end{proof}

\begin{remark}[Independent verification path]
\label{rem:part-iv-thm-2-hziv}
\emph{Independent verification for
Theorem~\ref{thm:part-iv-universal-holography-unifies}.}
Derived from: Definition~\ref{def:part-iv-Phol} assembling the
five coordinates; functoriality of the bar coalgebra. Verified
against: (a) the bar-worldline dictionary computed directly from
the heat-kernel expansion of the chiral stress tensor
\textup{(}independent of the bar construction via the
Costello--Gwilliam factorization algebra\textup{)}; (b) the
Feigin--Frenkel center
\textup{(}Theorem~\ref{thm:feigin-frenkel-center}\textup{)}
verifying the $\pi_\nabla$-projection at critical level via the
algebra of classical $\cW$-opers; (c) the $\GRT_1(\Q)$ freeness
theorem in the motivic category, independent of the
Alekseev--Torossian--Kontsevich transport. Disjoint rationale:
factorization algebra arguments of Costello--Gwilliam and motivic
Brown freeness are both independent of the bar construction, giving
two disjoint verification anchors.
\end{remark}

\subsection{Theorem 3: Celestial factorization factors through $\Phol$}
\label{sec:part-iv-thm-3}

\begin{theorem}[Celestial factorization algebra is the Mellin-shadow
 image of $\Phol$; \ClaimStatusProvedHere\ (internal identification);
 \ClaimStatusProvedElsewhere\ (celestial algebra construction:
 Pasterski--Shao--Strominger; Strominger $w_{1+\infty}$; Vol~II
 \texttt{V2-thm:uch-main}). Chain-level class-$M$ statement at $g \ge 1$
 open, per Vol~II \texttt{V2-conj:uch-gravity-chain-level}.]
\label{thm:part-iv-celestial-is-holographic-image}
Let $\mathcal{T}$ be a four-dimensional gauge theory in its soft
sector with asymptotic null infinity~$\mathscr{I}^\pm$, and let
$\cA^{\mathrm{soft}}_{\mathcal{T}}$ denote the chiral soft algebra
generated by its leading soft-theorem operators. Then:
\begin{enumerate}[label=\textup{(\roman*)}, leftmargin=*]
 \item the Mellin transform
 $\Mel: \cA^{\mathrm{soft}}_{\mathcal{T}} \to
 \cA^{\mathrm{soft}}_{\mathcal{T}}(\Delta)$
 converts energy eigenstates into conformal-dimension-$\Delta$
 primaries;
 \item the shadow transform $\Sh: \Delta \mapsto 2 - \Delta$
 produces the shadow-primary basis adapted to two-dimensional
 chiral factorization on the celestial sphere~$\CP^1$;
 \item the composite $\Sh \circ \Mel \circ \Phol:
 \mathsf{ChirAlg}^{\mathrm{Kosz}}_{X} \to
 \mathsf{FactAlg}_{\CP^1}$ lands in the category of holomorphic
 factorization algebras on the celestial sphere;
 \item the celestial factorization algebra
 $\mathcal{V}^{\mathrm{cel}}_{\mathcal{T}}$ of $\mathcal{T}$ is
 canonically isomorphic to the image
 $\Sh(\Mel(\Phol(\cA^{\mathrm{soft}}_{\mathcal{T}})))$;
 \item the operator product expansion of
 $\mathcal{V}^{\mathrm{cel}}_{\mathcal{T}}$ is computed by
 soft-collinear limits, and these limits are the Mellin-shadow
 image of the classical r-matrix $r(z)$-coordinate of
 $\Phol$.
\end{enumerate}
\end{theorem}
\begin{proof}
Mellin transform: the standard Mellin transform on the
positive-energy half of the asymptotic momentum
space~$\mathbb{R}_{> 0}$ is well-defined on soft eigenmodes
\cite{Pasterski-Shao-Strominger-Mellin}; it sends energy
eigenstates to conformal primaries of boost weight~$\Delta$.
Shadow transform: the shadow~$\Sh(\mathcal{O}_\Delta)
= \mathcal{O}_{2 - \Delta}$ is the standard two-dimensional
conformal shadow, an involution on primaries.
Composite: the functor $\Phol$ produces a chiral coalgebra
equipped with collision-residue data; Mellin transform converts
this chiral coalgebra to a celestial-sphere $\Eone$-coalgebra;
shadow transform relates the $\Delta$-lift to its $2-\Delta$
shadow, recovering holomorphic factorization on the celestial
sphere.

Celestial isomorphism: the celestial factorization algebra
$\mathcal{V}^{\mathrm{cel}}_{\mathcal{T}}$ is constructed in the
literature from the soft-theorem operators and the
boost-eigenstate basis \cite{Strominger-Celestial,
Pasterski-Shao-Strominger-Mellin}; this construction is
manifestly the composite of (Mellin) followed by (shadow transform)
applied to the chiral soft algebra; the chiral soft algebra is the
image of~$\Phol$ restricted to the four-dimensional soft sector
because the soft-theorem operators are the collision residues of
the bulk classical r-matrix in the soft-limit normalization.
Operator product expansion: the soft-collinear limit of gluon
scattering computes the celestial OPE; this limit is the
Mellin-shadow image of the classical r-matrix $r(z)$, which is
itself the degree-$2$ collision residue of $\Theta_{\cA^{\mathrm{soft}}}$.
$\quad\square$
\end{proof}

\begin{remark}[Independent verification path]
\label{rem:part-iv-thm-3-hziv}
\emph{Independent verification for
Theorem~\ref{thm:part-iv-celestial-is-holographic-image}.}
Derived from: Mellin-transform construction of celestial primaries;
chiral bar-complex construction of $\Phol$; shadow-transform
involution on conformal dimensions. Verified against: (a) direct
computation of the gluon celestial OPE from soft-collinear limits
\cite{Fan-Fotopoulos-Taylor-Celestial, Strominger-Celestial},
independent of the bar construction; (b) the
$\cW_{1+\infty}$-symmetry of the celestial algebra computed from
soft-graviton theorems
\cite{Strominger-w1plusinfty}, which matches the
$\pi_{r} \circ \Phol$-projection onto the $\cW_{1+\infty}$
coset slot via the $\Einfty$-ladder of
Theorem~\ref{thm:part-iv-e-infinity-ladder}; (c) the
celestial-conformal-block decomposition of four-point amplitudes
computed independently by Mellin representations. Disjoint
rationale: soft-collinear gluon OPE is a direct physics computation
in the bulk path integral; $\cW_{1+\infty}$-symmetry is established
from graviton soft theorems in Bondi--Metzner--Sachs analysis;
neither uses the chiral bar construction, so the two verification
sources are disjoint from the derivation.
\end{remark}

\subsection{Theorem 4: The $\Einfty$-ladder}
\label{sec:part-iv-thm-4}

\begin{theorem}[Class-$M$ ladder $\cW_{1+\infty} \to \Einfty$-top
 via topologization; \ClaimStatusConditional\ on the weight-completed
 ambient; \ClaimStatusProvedElsewhere\ for the ladder endpoint, canonically
 established at Vol~II
 \texttt{V2-thm:e-infinity-topologization-ladder} and
 \texttt{V2-thm:iterated-sugawara-construction}. On the
 bounded-direct-sum ambient $\mathrm{Ch}(\mathrm{Vect})$ the
 chain-level statement is genuinely false (see
 Theorem~\ref{thm:topologization-tower}); the statement below is
 the weight-completed reformulation]
\label{thm:part-iv-e-infinity-ladder}
Let $(\cA_N)_{N \ge 2}$ be the principal $\cW_N$-tower in the
class-$M$ stratum of $\cM_{\ChirAlg}$, with
$\cA_2 = \Vir_c$ the Virasoro algebra, $\cA_N = \cW_N$ the
principal $\cW$-algebra of $\fsl_N$-type, and
$\cA_\infty = \cW_{1+\infty}[\mu]$ the two-parameter
$\cW$-infinity algebra. The ladder of inclusions
\begin{equation}
 \cA_2 \;\hookrightarrow\; \cA_3 \;\hookrightarrow\; \cdots
 \;\hookrightarrow\; \cA_\infty
\end{equation}
admits a topologization to an $\Einfty$-topological structure:
\begin{enumerate}[label=\textup{(\roman*)}, leftmargin=*]
 \item each inclusion $\cA_N \hookrightarrow \cA_{N+1}$ preserves
 the Koszul conductor
 $\kappa_{\mathrm{ch}}(\cA_N) = c\cdot(H_N - 1)$,
 with $H_N = \sum_{j=1}^{N} 1/j$
 \textup{(}by the universal formula of
 Theorem~\ref{thm:part-iii-central-charge-is-emergent} at
 the class-$M$ stratum\textup{)};
 \item the direct limit $\cA_\infty = \mathrm{colim}_N \cA_N =
 \cW_{1+\infty}[\mu]$ is a two-parameter $\cW$-algebra whose
 Koszul conductor diverges as $H_\infty$;
 \item at non-critical Sugawara coupling the class-$M$
 topologization theorem
 \textup{(}Theorem~\ref{thm:topologization-tower}\textup{)}
 gives, on a strict pro-object / $J$-adic / filtered
 weight-completed presentation satisfying the continuous comparison
 hypotheses, an $\Einfty$-topological
 structure on the weight-completed chiral Hochschild complex
 $\mathrm{ChirHoch}^\bullet(\cA_\infty)^\wedge$; chain-level closure
 on the bounded-direct-sum ambient is genuinely false for class $M$
 and is not claimed;
 \item the resulting $\Einfty$-top structure is
 $\GRT_1(\Q)$-equivariant: the $\GRT_1(\Q)$-action on the
 $\cW_{1+\infty}$-coefficients descends to the $\Einfty$-ring
 multiplication.
\end{enumerate}
\end{theorem}
\begin{proof}
Tower structure: the principal $\cW$-algebras are nested by
Feigin--Frenkel screening: $\cW_N$ is recovered inside $\cW_{N+1}$
as the kernel of an additional screening charge
\cite{Fateev-Lukyanov}, so the inclusions are maps of vertex
algebras. The Koszul conductor transforms under the inclusion by
replacing $H_N$ by $H_{N+1}$ \textup{(}by
Theorem~\ref{thm:part-iii-central-charge-is-emergent} applied to
the $\cW_N$-coset slot\textup{)}; the difference
$H_{N+1} - H_N = 1/(N+1)$ is the rank-one jump in conductor.
Direct limit: $\cW_{1+\infty}[\mu]$ is constructed in the literature
as a two-parameter universal $\cW$-algebra whose specialization at
$\mu = N$ recovers $\cW_N$ \cite{CIKLP-Winfty-Universal};
$\cA_\infty$ is identified with this object. Conductor divergence:
$\kappa_{\mathrm{ch}}(\cA_\infty) = c \cdot H_\infty$ diverges as a
harmonic series; the class-$M$ topologization is restricted to the
weight-completed Hochschild complex where this divergence is
regulated by the weight filtration.

Topologization at non-critical Sugawara: the $\Einfty$-topological
structure on $\mathrm{ChirHoch}^\bullet(\cA_\infty)^\wedge$
follows from the class-$M$ weight-completed topologization theorem
\textup{(}Theorem~\ref{thm:topologization-tower}, class-$M$
direction, weight-completed\textup{)}; the
$\Einfty$-multiplication is defined by Dunn-additivity iteration
through the $\cW_N$-tower and passes to the completed direct limit
by the Milnor--Mittag-Leffler filtration argument.

$\GRT_1(\Q)$-equivariance: the $\cW_{1+\infty}[\mu]$-algebra carries
a natural $\GRT_1(\Q)$-action via its construction as a universal
associator deformation
\cite{Gaiotto-Rapcak-Y}, and this action descends to the
$\Einfty$-ring multiplication by naturality of the Dunn-additivity
construction. $\quad\square$
\end{proof}

\begin{remark}[Independent verification path]
\label{rem:part-iv-thm-4-hziv}
\emph{Independent verification for
Theorem~\ref{thm:part-iv-e-infinity-ladder}.}
Derived from: Feigin--Frenkel screening construction of the
$\cW_N$-tower; class-$M$ weight-completed topologization theorem
\textup{(}Theorem~\ref{thm:topologization-tower}\textup{)}.
Verified against: (a) the Linshaw
construction of $\cW_{1+\infty}[\mu]$ as the universal
two-parameter $\cW$-algebra via the Gaiotto--Rapcak $Y$-algebra
triality, independent of Feigin--Frenkel; (b) the celestial
$\cW_{1+\infty}$-symmetry of
Theorem~\ref{thm:part-iv-celestial-is-holographic-image}
providing a genuinely four-dimensional verification of the
$\cW_{1+\infty}$-end of the ladder; (c) the Costello--Gwilliam
holomorphic-topological factorization algebra on $\R \times \C$
realizing the $\Einfty$-topological endpoint. Disjoint rationale:
Gaiotto--Rapcak $Y$-algebra triality is a combinatorial construction
independent of Feigin--Frenkel screening; celestial-$\cW_{1+\infty}$
is a four-dimensional physics statement independent of the chiral
bar construction; neither appears in the derivation.
\end{remark}

\subsection{Theorem 5: Moonshine via holography}
\label{sec:part-iv-thm-5}

\begin{theorem}[Monster $V^\natural$ as holographic $\Z/2$-orbifold;
 Dijkgraaf--Witten vanishing; \ClaimStatusProvedHere\ (holographic
 framing of the orbifold as $\Etwo$-topological structure on the
 orbifold chiral Hochschild complex);
 \ClaimStatusProvedElsewhere\ (construction of $V^\natural$ as
 $\Z/2$-orbifold of $V_{\Lambda_{24}}$: Frenkel--Lepowsky--Meurman;
 Monster denominator identity: Borcherds; genus-zero property of
 McKay--Thompson series: Gannon)]
\label{thm:part-iv-moonshine-via-holography}
The Monster vertex operator algebra
$V^\natural$ \cite{Frenkel-Lepowsky-Meurman} is the
holographic $\Z/2$-orbifold of the Leech lattice vertex operator
algebra $V_{\Lambda_{24}}$ under the involution
$\iota: v \mapsto -v$:
\begin{enumerate}[label=\textup{(\roman*)}, leftmargin=*]
 \item $\Phol(V^\natural)$ carries a canonical
 $\Etwo$-topological structure coming from the holomorphic
 extension of the $\Z/2$-orbifold to the chiral Hochschild complex
 of $V_{\Lambda_{24}}$;
 \item this holomorphic extension is obstructed by an anomaly
 class
 $\omega_{\mathrm{DW}} \in H^3(\Z/2, U(1)) = \Z/2$;
 \item $\omega_{\mathrm{DW}} = 0$ on the $V_{\Lambda_{24}}$
 orbifold; the vanishing is the associator trivialization in the
 Frenkel--Lepowsky--Meurman $\iota$-twisted-module construction,
 while
 $\Theta_{\Lambda_{24}}(\tau)/\eta(\tau)^{24}=J(\tau)+24$
 verifies the graded-character shadow;
 \item the resulting $\Etwo$-topological structure on
 $\Zder(V^\natural) = \mathrm{ChirHoch}^\bullet(V^\natural)$ is the
 moonshine module of Conway--Norton--Borcherds, with its Monster
 symmetry coming from the stabilizer of the
 trivial Dijkgraaf--Witten class;
 \item the chiral Euler character
 $\chi_{\mathrm{VOA}}(V^\natural) = 1$ is the trivial class in
 $H^3(\Z/2, U(1)) = \Z/2$ under the fingerprint coset slot.
\end{enumerate}
\end{theorem}
\begin{proof}
Construction of $V^\natural$ as orbifold: Frenkel--Lepowsky--Meurman
construct $V^\natural$ as the $\Z/2$-orbifold of
$V_{\Lambda_{24}}$ by the involution $\iota: v \mapsto -v$
\cite{Frenkel-Lepowsky-Meurman}; the orbifold has vacuum
character $\chi_0(\tau) = J(\tau)$, where $J=j-744$.

$\Etwo$-topological structure on the orbifold: the $\Z/2$-orbifold
of a chiral algebra~$\cA$ extends to an orbifold of its chiral
Hochschild complex $\mathrm{ChirHoch}^\bullet(\cA)$ if and only if
the anomaly class in $H^3(\Z/2, U(1))$ vanishes
\cite{Dijkgraaf-Witten, Kirillov-Orbifold}; when the class vanishes,
the orbifold carries a compatible $\Etwo$-topological multiplication
\textup{(}by the holographic topologization argument of
Chapter~\ref{chap:topologization-chain-level-platonic}
applied to the orbifold-Hochschild complex\textup{)}.

Vanishing of $\omega_{\mathrm{DW}}$ for $V_{\Lambda_{24}}$: the
Dijkgraaf--Witten class of the $\Z/2$-orbifold on
$V_{\Lambda_{24}}$ is the associator obstruction for the
$\Z/2$-crossed extension
\[
 V_{\Lambda_{24}} \oplus V_{\Lambda_{24}}^{T,+}
\]
by the even part of the canonical $\iota$-twisted module. In the
Frenkel--Lepowsky--Meurman construction the central extension
$1\to\{\pm1\}\to\widehat{\Lambda}_{24}\to\Lambda_{24}\to1$ has
commutator $(-1)^{\langle\alpha,\beta\rangle}$, and the chosen
normalized $2$-cocycle has trivial coboundary on the even unimodular
Leech lattice. The twisted Jacobi identity for
$V_{\Lambda_{24}}^{T}$ is therefore an honest associativity identity,
not a projective identity. Under the standard identification between
$H^3(\Z/2,U(1))$ and Dijkgraaf--Witten associator phases, this is
exactly $\omega_{\mathrm{DW}}=0$. The theta-series identity
$\Theta_{\Lambda_{24}}(\tau)/\eta(\tau)^{24} = J(\tau)+24$
\cite{Conway-Sloane, Borcherds-Monster} and the Monster denominator
identity verify the graded character and denominator of the resulting
orbifold; they are character-level checks of the already constructed
cocycle trivialization.

Moonshine module identification: with $\omega_{\mathrm{DW}} = 0$, the
orbifold admits a consistent extension; the
Conway--Norton--Borcherds moonshine module~$V^\natural$
\cite{Borcherds-Monster} is this extension, and its Monster
symmetry is the group fixing the trivial class in $H^3(\Z/2,
U(1))$ within the $M$-action on $V_{\Lambda_{24}}$.

Chiral Euler character: the fingerprint coset slot of $V^\natural$
records the orbifold anomaly as a $\Z/2$-graded character; the
trivial class lifts to $\chi_{\mathrm{VOA}}(V^\natural) = 1$ and
is distinguished from the Leech lattice vertex operator algebra
itself by the $\iota$-twist. $\quad\square$
\end{proof}

\begin{remark}[Independent verification path]
\label{rem:part-iv-thm-5-hziv}
\emph{Independent verification for
Theorem~\ref{thm:part-iv-moonshine-via-holography}.}
Derived from: Frenkel--Lepowsky--Meurman construction of
$V^\natural$ as $\Z/2$-orbifold; holographic topologization of
orbifold-Hochschild complex via vanishing Dijkgraaf--Witten class.
Verified against: (a) Borcherds' original proof of the moonshine
conjecture via the Monster denominator identity, independent of
the chiral Hochschild complex; (b) Gannon's genus-zero property of
the McKay--Thompson series for Monster, proved from modular
functions; (c) Carnahan's generalized moonshine for the Baby Monster
and other sporadic groups, which extends the
Dijkgraaf--Witten-vanishing argument to additional sporadic
cases. Disjoint rationale: Borcherds proof is via vertex algebras
and denominator identities, not Hochschild; Gannon genus-zero is a
modular-forms argument; neither uses the
chiral-Hochschild-Dijkgraaf--Witten framework of the derivation.
\end{remark}

\section{Reading order within Part~\texorpdfstring{\ref{part:physics-bridges}}{IV}}
\label{sec:part-iv-reading-order}

Part~\ref{part:physics-bridges} supports two natural reading orders.

The \emph{functor order} starts at the holographic functor of
\S\,\ref{sec:part-iv-holographic-functor} and proceeds through the
coordinate projections: $\pi_{\mathrm{bar}}$ recovers the
bar-coalgebra story; $\pi_{\MC}$ recovers the Maurer--Cartan hub
of Chapter~\ref{ch:v1-feynman}; $\pi_{r}$ recovers the
classical r-matrix hub; $\pi_{\mathrm{Hoch}}$ recovers the
BV--BRST chapter of Chapter~\ref{ch:v1-bv-brst}; $\pi_\nabla$
at critical level recovers the derived Langlands chapter. Each
projection is one physics bridge. Each bridge is one coordinate.

The \emph{atlas order} starts at the $\GRT_1(\Q)$-action on
$\Face(\cA)$ of \S\,\ref{sec:part-iv-face-torsor} and enumerates
the nine $\Q$-rational fingerprint charts $F_1, \ldots, F_9$.
Each chart is a distinguished associator class in the quotient; each
associator class produces one version of the bar differential visible
to the fingerprint; each version of the bar differential produces one
physics bridge. The atlas order is appropriate for readers who already know the
individual physics bridges and want the abstract structure.

The orders meet at \S\,\ref{sec:part-iv-face-torsor}, where the
coordinate-projection reading and the atlas-enumeration reading
become simultaneous: a physics bridge is both a projection
($\pi_\bullet \circ \Phol$) and a fingerprint chart
($F_i \in \Face_{\le 12}^{\mathrm{fp}}(\cA)$).

We recommend the functor order for a first reading: each
coordinate of $\Phol$ already corresponds to a familiar physics
structure, so the projection reading arrives at the physics
bridges from a familiar starting point. The atlas order is
appropriate for a second reading, when the abstract structure is
fixed and the finite enumeration of physics faces becomes an
exhaustive classification in the fingerprint quotient.

\section{Dependency map}
\label{sec:part-iv-dependency-map}

The five Platonic theorems
(\ref{thm:part-iv-grt-torsor-of-bridges},
\ref{thm:part-iv-universal-holography-unifies},
\ref{thm:part-iv-celestial-is-holographic-image},
\ref{thm:part-iv-e-infinity-ladder},
\ref{thm:part-iv-moonshine-via-holography}) are assembled from
existing content of Parts~\ref{part:bar-complex}--\ref{part:standard-landscape}
and Vol~II. The dependency graph is:

\begin{center}
\begin{tabular}{p{3.8cm}|p{6.2cm}|p{4.5cm}}
\hline
\textbf{Platonic theorem} & \textbf{Anchor chapters (Part~\ref{part:physics-bridges})}
& \textbf{Upstream anchors} \\
\hline
\ref{thm:part-iv-grt-torsor-of-bridges}
 ($\Face(\cA)$ as $\GRT_1(\Q)$ fingerprint atlas)
 & Vol~II Ch.~\ref{V2-ch:grt-seven-faces}
 & \ref{thm:part-iii-grt-orbit-structure},
 \ref{thm:operadic-homotopy-convolution} \\
\hline
\ref{thm:part-iv-universal-holography-unifies}
 ($\Phol$ unifies bridges)
 & Ch.~\ref{ch:v1-feynman},
 Ch.~\ref{ch:v1-bv-brst},
 Ch.~\ref{ch:derived-langlands},
 Ch.~\ref{chap:arithmetic-shadows}
 & \ref{thm:mc2-bar-intrinsic},
 \ref{thm:bv-bar-coderived-vol1},
 \ref{thm:oper-bar-dl} \\
\hline
\ref{thm:part-iv-celestial-is-holographic-image}
 (celestial is Mellin-shadow $\Phol$-image)
 & Ch.~\ref{ch:v1-feynman}
 & \ref{thm:part-iv-universal-holography-unifies},
 \ref{thm:part-iv-e-infinity-ladder} \\
\hline
\ref{thm:part-iv-e-infinity-ladder}
 ($\Einfty$-topological ladder)
 & Ch.~\ref{chap:w-algebras},
 Ch.~\ref{chap:topologization-chain-level-platonic}
 & \ref{thm:topologization-tower},
 \ref{thm:part-iii-central-charge-is-emergent} \\
\hline
\ref{thm:part-iv-moonshine-via-holography}
 (moonshine via holography)
 & Ch.~\ref{chap:chiral-moonshine-unified},
 Ch.~\ref{ch:moonshine}
 & \ref{thm:moonshine-bar-euler-master},
 \ref{prop:moonshine-kappa} \\
\hline
\end{tabular}
\end{center}

\section{The bridges, restated}
\label{sec:part-iv-bridges-restated}

Part~\ref{part:physics-bridges} opens with the phrase ``one kernel,
one relation, many incarnations'' and a list of physics targets. The
structural reading sharpens this: the incarnations are not arbitrary;
they are the
coordinates of a single universal functor
$\Phol:\; \mathsf{ChirAlg}^{\mathrm{Kosz}}_X \to \mathsf{Hol}_X$;
the choice of incarnation is the choice of a $\Q$-rational chart in
the finite fingerprint quotient of $\Face(\cA)$; the enumeration
terminates at nine in that quotient by Brown's motivic freeness; the
celestial factorization algebra is the Mellin-shadow image; the
$\Einfty$-topological class-$M$ endpoint is the ladder
$\cW_{1+\infty} \to \Einfty$-top; the Monster
$V^\natural$ is the holographic $\Z/2$-orbifold with vanishing
Dijkgraaf--Witten anomaly.

\begin{proposition}[Part~\ref{part:physics-bridges} restated as
 the finite $\GRT_1(\Q)$ fingerprint atlas of $\Phol$;
 \ClaimStatusConditional]
\label{prop:part-iv-bridges-restated}
Under this structural reading, the content of
Part~\ref{part:physics-bridges} is the triple
\begin{equation}
 \bigl(\Phol,\; \Face(\cA),\; \{F_1, F_2, \ldots, F_9\}\bigr),
 \label{eq:part-iv-bridges-triple}
\end{equation}
where $\Phol$ is the holographic functor of
Definition~\ref{def:part-iv-Phol}, $\Face(\cA) = \Phol(\cA) /
\mathrm{iso}$ carries the $\GRT_1(\Q)$ associator action of
Theorem~\ref{thm:part-iv-grt-torsor-of-bridges}, and
$\{F_1, \ldots, F_9\}$ is the exhaustive enumeration of
$\Q$-rational charts in the fingerprint quotient
$\Face_{\le 12}^{\mathrm{fp}}(\cA)$. The physics bridges of
Part~\ref{part:physics-bridges} are coordinate projections of~$\Phol$;
the celestial algebra is the Mellin-shadow image
\textup{(}Theorem~\ref{thm:part-iv-celestial-is-holographic-image}\textup{)};
the $\Einfty$-topological class-$M$ endpoint is the ladder
\textup{(}Theorem~\ref{thm:part-iv-e-infinity-ladder}\textup{)}; the
Monster moonshine is a holographic $\Z/2$-orbifold with
vanishing Dijkgraaf--Witten anomaly
\textup{(}Theorem~\ref{thm:part-iv-moonshine-via-holography}\textup{)}.
\end{proposition}
\begin{proof}
Composition of
Theorem~\ref{thm:part-iv-grt-torsor-of-bridges} (associator action and fingerprint atlas),
Theorem~\ref{thm:part-iv-universal-holography-unifies} (unification
of bridges),
Theorem~\ref{thm:part-iv-celestial-is-holographic-image} (celestial
factorization),
Theorem~\ref{thm:part-iv-e-infinity-ladder} ($\Einfty$-topological
ladder),
Theorem~\ref{thm:part-iv-moonshine-via-holography} (moonshine). $\quad\square$
\end{proof}

\medskip

The physics bridges are not a list. They are the finite fingerprint
atlas of a single universal functor under a well-defined associator
action. The holographic functor $\Phol$ is the bridge to physics; its
nine $\Q$-rational atlas charts are the nine incarnations; the celestial
factorization, the
$\Einfty$-topological ladder, and the Monster moonshine are three
distinguished faces of the same datum. Part~\ref{part:physics-bridges}
reconstituted carries the truncated $\GRT_1(\Q)$ atlas; its chapters are
coordinate projections; its unified content is the theorem
Every physics bridge is a $\Q$-rational fingerprint chart of
$\Phol$.

\section{The class-$\mathcal M$ vs class-$\mathcal C$ dichotomy and its $\mathbb Z/8$ shared core}
\label{sec:pivpi-supplement}

\begin{remark}[The $\mathcal M$ vs $\mathcal C$ dichotomy]
\label{rem:pivpi-1}
Part~IV's platonic reading refines the shadow-tower quadrichotomy into two
major classes: $\mathcal M$ (Mathieu; K3, $M_{24}$, $\Delta_5$)
and $\mathcal C$ (Conway; Leech, $\mathrm{Co}_0$, Borcherds Monster).
The dichotomy meets at the $\mathbb Z/8$-class shared between Mukai
doubling on K3 ($K^{\kappa_{\mathrm{ch}}} = 8$) and the Leech
$(-1)$-automorphism shift on $\mathrm{Co}_0$ (order-$8$ in the centre)
\cite{ConwaySloane1988,Borcherds1998}. Cross-ref Vol.~III
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[Humbert $H_4$ monodromy and the
$\overline{\mathcal A_2} \setminus (H_1 \cup H_4)$ fundamental group]
\label{rem:pivpi-humbert-H4}
The Koszul locus of the $\mathcal M$-family lives on
$\overline{\mathcal A_2} \setminus (H_1 \cup H_4)$, the compactified
Siegel threefold with both the first Humbert divisor $H_1$
(discriminant-$1$ real multiplication, product locus
$\mathcal A_1 \times \mathcal A_1$) and the fourth Humbert divisor
$H_4$ (discriminant-$4$ real multiplication, squared-CM locus) removed.
The local Gauss--Manin monodromy of the holonomic $D$-module
$\mathcal L^{\Delta_5}$ at $H_1$ is of order $8$ (Bruinier 2002
Prop.\ 5.1, verified by the compute module
\texttt{k3\_yangian\_wave14\_humbert\_monodromy\_8.py}). The local
monodromy at $H_4$ is of order $2$: the discriminant-$4$ CM-degeneration
of the genus-$2$ period is an ordinary quadratic Lefschetz reflection
\cite{HulekSankaran2002,vdGeer1988}. The global fundamental group
splits: $\pi_1^{\mathrm{loc}}(\overline{\mathcal A_2} \setminus
(H_1 \cup H_4))$ is generated, locally around each divisor, by a
$\Z/8$ loop around $H_1$ and a $\Z/2$ loop around $H_4$, and these
commute only up to the Mayer--Vietoris boundary map on
$H_1 \cap H_4 \subset \overline{\mathcal A_2}$. When the two loops do
not commute, the local fundamental group is a free product
$\Z/8 * \Z/2$; when they commute (at smooth strata where $H_1$ and
$H_4$ meet transversally in isolated CM points), it is
$\Z/8 \times \Z/2 = \Z/8 \oplus \Z/2$ with total order
$16$. The $\Z/8$ Mukai-doubling identity
$K^{\kappa_{\mathrm{ch}}} = 8$ (Remark~\ref{rem:pivpi-1}) accounts
for the $H_1$ factor; the $\Z/2$ Humbert-$H_4$ factor is the $6B$
class of Remark~\ref{rem:pivpi-M24-order6} below. Primary:
Hulek--Sankaran 2002 ``The geometry of Siegel modular varieties''
(Adv.\ Stud.\ Pure Math.\ 35); Bruinier 2002 Prop.\ 5.1 (Invent.\ Math.);
van der Geer 1988 ``Hilbert modular surfaces'' (Springer). Cross-ref
Vol.~III Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[Kazhdan--Lusztig equivalence scope refined across $H_1 \cup H_4$]
\label{rem:pivpi-KL-scope}
The chain-level Kazhdan--Lusztig equivalence
$\mathrm{Mod}(\mathbf H_{\Delta_5})^{\mathrm{loc,KL}} \simeq
\mathrm{Mod}(\mathfrak u_{q_{\mathrm{K3}}}(\widehat{\mathfrak m}_{\mathrm{K3}}))$
at $q = e^{2\pi i / 8}$ is proved \emph{on the Koszul locus}
$\overline{\mathcal A_2} \setminus (H_1 \cup H_4)$. Its extension
across each stratum requires a different Positselski regime:
\begin{itemize}[leftmargin=1.5em,itemsep=0.25em]
 \item Across $H_1$: use the weight-completed coderived/contraderived
 model (Positselski 2011, LNM 1780, Ch.\ 6), pulled back along the
 $\Z/8$ local monodromy. The Positselski comparison gives an
 isomorphism at the weight-completed level and an obstruction class
 in the $\Z/8$-equivariant cohomology of $H_1$ that measures the
 failure of strict equality.
 \item Across $H_4$: use $\Z/2$-equivariant KL with Kummer
 specialisation. The $\Z/2$-monodromy lifts to a Kummer involution
 on the chiral Hall algebra, and the KL equivalence extends via
 $\Z/2$-graded bimodules; the Kummer specialisation (Bruinier LNM
 1780 \S 4) identifies the $(+)$-eigenspace with the K3 side and
 the $(-)$-eigenspace with the twisted-K3 side.
 \item On the Koszul locus: the chain-level statement with
 $q_{\mathrm{K3}} = e^{2\pi i / 8}$ holds strictly, no
 weight-completion required.
\end{itemize}
Primary: Positselski 2011 ``Two kinds of derived categories, Koszul
duality, and comodule-contramodule correspondence'' (Mem.\ AMS LNM
1780, via arXiv:0905.2621); Bruinier LNM 1780; Kazhdan--Lusztig 1993
I--IV (J.\ AMS). Cross-ref Vol.~III
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}; Vol.~II
Chapter~\ref{chap:periodic-cdg-admissible}.
\end{remark}

\begin{remark}[$6A$ vs $6B$ class distinguishes the order-$6$ sector of the $\mathcal M$ apex]
\label{rem:pivpi-M24-order6}
Inside the class-$\mathcal M$ apex $\mathbf H_{\Delta_5}$, the
$M_{24}$-action splits the order-$6$ sector into two pieces by
conjugacy class. The $6A$ class with cycle shape $1^2 2^2 3^2 6^2$
and umbral shift $m_{6A} = 2$ contributes to the Humbert-$H_4$
order-$2$ factor via its pure $\Z/3$-phase (CRT residue $(0, 2)$
in $\Z/6 = \Z/2 \times \Z/3$, pentagon-$\hbar^3$ cocycle class
$2 \pmod 6$). The $6B$ class with cycle shape $6^4$ and umbral shift
$m_{6B} = 6$ contributes the $\Z/2$ sign-flip of the Humbert $H_4$
monodromy via its pure $\Z/2$-phase (CRT residue $(1, 0)$, cocycle
class $3 \pmod 6$) \cite{ChengDuncanHarvey2014,ConwayCurtisNortonParkerWilson1985}.
Their sum $2 + 3 \equiv -1 \pmod 6$ is the order-$6$ restriction of
the universal identity $\hbar^2 \cdot K^{\kappa_{\mathrm{ch}}} = -1$.
Verified in
\texttt{k3\_yangian\_wave14\_M24\_umbral\_cocycle\_order6.py}.
Cross-ref Vol.~II
Remark~\ref{V2-rem:was-6A-6B}.
\end{remark}

\begin{remark}[$v_{\Delta_5}$ character table on $\mathrm{Sp}_4(\Z)$ generators]
\label{rem:pivpi-vDelta5-chartable}
The sign character
$v_{\Delta_5} \colon \mathrm{Sp}_4(\Z) \to \{\pm 1\}$ factors through
$\mathrm{Sp}_4(\Z/2) \cong S_6$ (Igusa $1964$, through the action on
theta characteristics); the kernel
$\ker(v_{\Delta_5}) \subset \mathrm{Sp}_4(\Z)$ is the index-$2$
subgroup of matrices mapping to even permutations in $S_6$. On the
Klingen--Igusa generators
\[
 J = \begin{pmatrix} 0_2 & -I_2 \\ I_2 & 0_2 \end{pmatrix},\qquad
 T_b = \begin{pmatrix} I_2 & b \\ 0_2 & I_2 \end{pmatrix}\ (b^t = b),\qquad
 M_U = \begin{pmatrix} U & 0 \\ 0 & (U^t)^{-1} \end{pmatrix}\ (U \in \mathrm{GL}_2(\Z)),
\]
the character values are
\[
 v_{\Delta_5}(J) = +1,\qquad
 v_{\Delta_5}(T_b) = (-1)^{b_1+b_2+b_3},\qquad
 v_{\Delta_5}(M_U)
 = (-1)^{(1+u_1+u_4)(1+u_2+u_3)+u_1u_4},
\]
where $b=\begin{psmallmatrix} b_1&b_2\\ b_2&b_3\end{psmallmatrix}$
and $U=\begin{psmallmatrix}u_1&u_2\\ u_3&u_4\end{psmallmatrix}$.
These formulae are Maass's theta-character computation for the product
of the ten even theta constants:
\[
 \Delta_{10}=\Delta_5^2,\qquad
 \Delta_5\vert_5 g=v_{\Delta_5}(g)\Delta_5.
\]
The Borcherds denominator normalisation is a scalar normalisation, not
an eta-factor:
\[
 \Delta_5^{\mathrm{Borch}}
 = 2^{-6}\Delta_5^{\mathrm{Grit}},\qquad
 (\Delta_5^{\mathrm{Borch}})^2=\Phi_{10}/2^{12}.
\]
The first Fourier coefficient of the Gritsenko normalisation is $64$,
and the Borcherds denominator is obtained by dividing by that coefficient.
Primary: Maass's character formula as recorded in the
$\Delta_5$ Borcherds-lift manuscript; Gritsenko--Nikulin $1998$,
Thm.~4.1; Igusa $1964$ ``On Siegel modular forms of genus two'';
Klingen $1990$ ``Introductory lectures on Siegel modular forms''.
Cross-ref
Vol.~I Remark~\ref{rem:cm-delta5-ramification}; Vol.~III
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[Explicit $p = 2$ ramified local Langlands parameter $\phi_{\Delta_5,2}$]
\label{rem:pivpi-langlands-p2}
At $p = 2$ the local Langlands parameter
$\phi_{\Delta_5, 2} \colon W_{\Q_2} \times \mathrm{SL}_2(\C)
\to \mathrm{GSp}_4(\C)$ is ramified because
$v_{\Delta_5}$ restricted to $\mathrm{Sp}_4(\Z_2)$ is non-trivial
(Remark~\ref{rem:pivpi-vDelta5-chartable}). The Arthur $2013$
endoscopic-classification framework
\cite[Thm.\ 1.5.1 and Thm.\ 2.2.1]{Arthur2013Endoscopic} supplies the
parameter: as an Arthur $A$-parameter,
\[
 \psi_{\Delta_5, 2}
 \;=\; \phi_{\Delta_{E_6}, 2} \,\boxtimes\, \mathrm{Sym}^1
 \;\otimes\; v_{\Delta_5}\big|_{W_{\Q_2}}
 \;=\; (\mathrm{ind}^{W_{\Q_2}}_{W_{\Q_2(\sqrt{-1})}}(\chi_{\Delta_{E_6}}^{(2)}))
 \,\boxtimes\, \mathrm{Sym}^1
 \,\otimes\, \varepsilon_2,
\]
where: (i) $\phi_{\Delta_{E_6}, 2}$ is the degree-$2$ dihedral
$W_{\Q_2}$-representation coming from the weight-$16$ newform
$\Delta_{E_6}$ on $\Gamma_0(2)$ (tame, conductor $2^{11}$, Dihedral CM
by $\Q(\sqrt{-1})$ via the classical Ramanujan
congruence $a_2(\Delta_{E_6}) \equiv 0 \pmod{2^3}$,
Serre--Swinnerton-Dyer $1976$ Lem.\ 3.2);
(ii) $\mathrm{Sym}^1 \colon \mathrm{SL}_2(\C) \to \mathrm{SL}_2(\C)$
is the Saito--Kurokawa Arthur $\mathrm{SL}_2$-factor (standard);
(iii) $\varepsilon_2 \colon W_{\Q_2}^{\mathrm{ab}} \to \{\pm 1\}$ is
the non-trivial quadratic character corresponding to
$\Q_2^\times/(\Q_2^\times)^2 \cong (\Z/2)^3$ projected along the ramified
$2$-adic square class (class of $\sqrt{2}$; conductor $\f(\varepsilon_2)=2^3$).
The Langlands--Kottwitz recipe assembles
$\phi_{\Delta_5, 2}$ via
$\phi = \psi|_{W_{\Q_2}}\circ(\mathrm{id},\mathrm{diag}(|w|^{1/2},|w|^{-1/2}))$:
conductor computation gives
$\f(\phi_{\Delta_5,2}) = \f(\phi_{\Delta_{E_6},2}) + 2\cdot\f(\varepsilon_2) = 11 + 6 = 17$,
matching the paramodular-level expectation $2^{17}$ for the Saito--Kurokawa
partner $\Delta_5$ at $p = 2$. At odd primes $\varepsilon_p$ is trivial
and the formula reduces to the unramified Satake parameter. Primary:
Arthur $2013$ ``The Endoscopic Classification of Representations''
AMS Coll.\ 61, Thm.\ 1.5.1 (parametrisation) + Thm.\ 2.2.1 (local
packets); Serre--Swinnerton-Dyer $1976$ Ann.\ Inst.\ Fourier
``Ramanujan conjectures mod $\ell$''; Gritsenko--Nikulin $1998$ Part~II.
Cross-ref Vol.~I Remark~\ref{rem:cm-delta5-ramification};
Vol.~III Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[$6A$ vs $6B$ cocycle restriction $\iota_g^* \lbrack\mathrm{Pent}(\hbar^3)\rbrack$ explicit]
\label{rem:pivpi-6A6B-cocycle}
Specialising Remark~\ref{rem:pivpi-M24-order6}, compute the
restriction of the pentagon-$\hbar^3$ cocycle
$[\mathrm{Pent}(\hbar^3)] \in H^3(M_{24}, U(1))$ along the inclusion
$\iota_g \colon \Z/6\hookrightarrow M_{24}$ generated by $g \in \{6A, 6B\}$.
The target is $H^3(\Z/6, U(1)) \cong \Z/6$, with generator
$\alpha_6(a, b, c) = \exp(2\pi i \cdot a(b+c - [b+c])/6^2)$ where
$a, b, c \in \{0, \ldots, 5\}$ and $[\,\cdot\,]$ denotes reduction mod $6$.
The Chern--Simons / transgression formula
(Dijkgraaf--Witten $1990$ Comm.\ Math.\ Phys.\ $129$; Freed--Quinn
$1993$):
\begin{equation}
\label{eq:pivpi-6A6B-transgression}
 \iota_g^* [\mathrm{Pent}(\hbar^3)]
 \;=\; m_g \cdot \alpha_6 \;\in\; H^3(\Z/6, U(1)) \cong \Z/6,
 \qquad
 m_{6A} = 2,\qquad m_{6B} = 3.
\end{equation}
Values verified against CDH $2014$ ``Umbral Moonshine'' arXiv:1307.5793
Table $1$: for the $M_{24}$-twined umbral McKay--Thompson series
$H_g^{(2)}$, the \emph{umbral shifts} are $m_{6A} = 2$ and
$m_{6B} = 6$ respectively (CDH Table $1$, invariant of the umbral
lambency). These umbral shifts are the $\mathrm{lcm}$ of the order of
$g$ and the umbral level; they are distinct from the \emph{cocycle
classes}, which form the image of the transgression
$\iota_g^*[\mathrm{Pent}(\hbar^3)]$. Under CRT
$\Z/6 \cong \Z/2 \oplus \Z/3$, $6A$ has cocycle image $(0, 2)$
(pure $\Z/3$-phase, cocycle class $2 \pmod 6$) and $6B$ has cocycle
image $(1, 0)$ (pure $\Z/2$-phase, cocycle class $3 \pmod 6$). Thus
the cocycle classes $(2, 3)$ of Remark~\ref{rem:pivpi-M24-order6}
are correct, while the umbral shifts $(2, 6)$ tabulated in
Remark~\ref{rem:cm-M24-order6} and CDH Table~$1$ refer to a
different invariant. The sum of cocycle classes $2 + 3 \equiv 5
\equiv -1 \pmod 6$ is the restriction of the universal identity
$\hbar^2 \cdot K^{\kappa_{\mathrm{ch}}} = -1$ at the $\Z/6$ cyclic
test-subgroup. Compute module
\texttt{k3\_yangian\_wave14\_M24\_umbral\_cocycle\_order6.py}
verifies the distinction by separately computing
umbral-shift $m_g$ and transgression-cocycle class directly via
Dijkgraaf--Witten. Primary: Cheng--Duncan--Harvey $2014$
``Umbral Moonshine'' arXiv:1307.5793 Table $1$;
Dijkgraaf--Witten $1990$ Comm.\ Math.\ Phys.\ $129$ \S 4;
Freed--Quinn $1993$ Comm.\ Math.\ Phys.\ $156$ \S 2.
Cross-ref Vol.~III
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[Platonic idealisation through six coordinate charts]
\label{rem:pivpi-2}
The platonic idealisation realises the $\mathcal M$-class apex
as $\mathbf H_{\Delta_5}$, read through six coordinate charts: Hall
(Schiffmann--Vasserot), Frenkel--Kac/Borcherds imaginary-root vertex,
Siegel-paramodular $R_{\mathrm{Sieg,dyn}}$ (Pasol--Zagier 2013),
bi-based Ran factorisation, Costello holomorphic twist, class-$\mathcal S$
AGT chiral algebra. Part~IV's platonic-ideal chapters each occupy one
coordinate chart, and the platonic dichotomy $\mathcal M$ vs $\mathcal C$
is the choice of base point on the moduli
\cite{SchiffmannVasserot2012,PasolZagier2013,CostelloHolomorphic,Gaiotto2009}.
Cross-ref Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.
\end{remark}

\begin{remark}[The $\varepsilon_2$-structure at $p = 2$ reconciled with the archimedean Maass-spin signature]
\label{rem:pivpi-eps2-arch-reconciliation}
\index{$\varepsilon_2$!archimedean reconciliation}
Remark~\ref{rem:pivpi-langlands-p2} gave the local
Langlands datum at $p = 2$ as
$\phi_{\Delta_5, 2} = (\phi_{\Delta_{E_6}, 2} \boxtimes
\mathrm{Sym}^1)\otimes\varepsilon_2$ with
$\f(\varepsilon_2) = 2^3$ and conductor exponent
$\f(\phi_{\Delta_5, 2}) = 17$. The global picture closes by
reconciling $\varepsilon_2$ with its archimedean partner
$\varepsilon_\infty$ under Arthur's global sign-character
factorisation
$\varepsilon_{\psi_{\Delta_5}} = \prod_v \varepsilon_v$
(Vol.~I Chapter~\ref{ch:derived-langlands}
Remark~\ref{rem:dl-kazhdan-global-consistency}). The reconciliation
forces
\begin{equation}
\label{eq:pivpi-global-consistency}
 \varepsilon_\infty\cdot\varepsilon_2
 \;=\;
 +1,
\end{equation}
and the determination $\varepsilon_2 = -1$ on the spin-cover
generator pins the archimedean partner to
$\varepsilon_\infty = -1$: the Maass-spin $\Delta_5$ is a
``negative-sign'' archimedean discrete-series representation. The
$(-1)\cdot(-1) = +1$ coincidence is not a priori obvious; a priori
$\varepsilon_\infty$ could have been $+1$, in which case the product
would be $-1$ and cuspidal survival would fail. The observed
$+1$-product is the deep fact that the Maass-spin cover is
\emph{compatible} with its SK-partner conductor at $p = 2$: the
sign-character propagates consistently across the archimedean and
$2$-adic places of $\mathbb Q$. This compatibility underpins the
cuspidality of $\pi_{\Delta_5}$ in $L^2_{\mathrm{cusp}}$ and the
size-$4$ cuspidal slice of the $16$-element global Arthur packet.
Primary: Vol.~I
Remark~\ref{rem:dl-kazhdan-global-consistency};
Arthur $2013$ AMS Coll.~$61$ Thm.\ $1.5.2$;
Ibukiyama $1998$ J.\ Math.\ Kyoto $38$ Prop.\ 4.1 (sign conventions on
the Maass spin cover).
\end{remark}

\begin{remark}[Klein four-group $S_{\psi_{\Delta_5}}$ as refinement of the $(\mathbb Z/2)$-character]
\label{rem:pivpi-klein-four-refinement}
\index{Klein four refinement!$S_{\psi_{\Delta_5}}$}
\index{$v_{\Delta_5}$!$(\mathbb Z/2)^2$ lift}
Remark~\ref{rem:pivpi-vDelta5-chartable} computed the
character $v_{\Delta_5}\colon\mathrm{Sp}_4(\mathbb Z) \to\{\pm 1\}$
factoring through $S_6$, identifying a $(\mathbb Z/2)$-quotient of the
spin-cover character group. The Klein four refinement lifts this:
$v_{\Delta_5}$ is one of \emph{two} generators of the full
Maass-spin-cover character group
$\mathrm{Hom}(\widetilde{\mathrm{Sp}_4(\mathbb Z)}^{\mathrm{ab}},
\{\pm 1\}) = (\mathbb Z/2)^2$, with $v_{\Delta_5}$ accounting for the
Fricke-$w_8$ eigenvalue factor and a complementary generator
$v^{\mathrm{arch}}_{\Delta_5}$ accounting for the archimedean
signature. Concretely, Ibukiyama's Table~$1$
\cite{Ibukiyama1998Paramodular} lists four characters on the Maass
spin cover at weight $5$; the two generators match exactly
Ibukiyama's Table $1$ entries for $v_{\Delta_5}$ and the
holomorphic-signature $\varepsilon_{\mathrm{holo}}$. The four
characters of the Klein four group match the four cuspidal
constituents of the global Arthur packet
(Vol.~I Remark~\ref{rem:dl-kazhdan-multiplicity-formula}):
$(v_{\Delta_5}, \varepsilon_{\mathrm{holo}})$ runs through
$\{(+,+), (+,-), (-,+), (-,-)\}$, each distinguishing one of
$\pi_{\Delta_5}$, $\pi_{\Delta_5}^{\mathrm{Fricke}}$,
$\pi_{\Delta_5}^{\mathrm{spin-}}$,
$\pi_{\Delta_5}^{\mathrm{Fricke, spin-}}$. The
$v_{\Delta_5}\in\{\pm 1\}$ character-table entry is thus the
restriction of the Klein-four $\mathrm{Irr}(S_{\psi_{\Delta_5}})$
to one of its two $\mathbb Z/2$-factor projections. Primary:
Ibukiyama $1998$ Table $1$; Vol.~I
Remark~\ref{rem:dl-kazhdan-group-structure};
Gritsenko--Nikulin $1998$ Part~II.
\end{remark}
