\providecommand{\cZ}{\mathcal{Z}}

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
\label{ch:preface}
\markboth{Preface}{Preface}

\vspace{1em}

\section*{1.\quad The bar construction on algebraic curves}
% ====================================================================

\subsection*{The $1$-form}

\noindent
Let $X$ be a smooth algebraic curve over $\mathbf{C}$.  On the configuration space
$C_2(X) = X \times X \setminus \Delta$, define the logarithmic $1$-form
\begin{equation}\label{eq:preface-eta}
\eta_{12} \;=\; d\log(z_1 - z_2) \;=\; \frac{dz_1 - dz_2}{z_1 - z_2}\,.
\end{equation}
This form has a simple pole along the diagonal $\Delta \subset X \times X$
with residue $1$.  The residue is intrinsic: it depends on no coordinate, no
metric, no level.  A double pole $dz/(z-w)^2$ transforms under coordinate
change and has no coordinate-independent residue.  A regular $1$-form on
$X \times X$ has residue zero along $\Delta$ and extracts nothing from the
collision.  The logarithmic derivative is the unique $1$-form on $C_2(X)$
with a first-order pole along $\Delta$ and conformally invariant residue.

On $C_3(X)$, the three pullbacks $\eta_{12}, \eta_{23}, \eta_{31}$ satisfy
the \emph{Arnold relation}
\begin{equation}\label{eq:preface-arnold}
\eta_{12} \wedge \eta_{23} \;+\; \eta_{23} \wedge \eta_{31}
\;+\; \eta_{31} \wedge \eta_{12} \;=\; 0\,.
\end{equation}
This is a differential-form restatement of the partial-fractions identity
\[
\frac{1}{(z_1 - z_2)(z_2 - z_3)}
\;+\; \frac{1}{(z_2 - z_3)(z_3 - z_1)}
\;+\; \frac{1}{(z_3 - z_1)(z_1 - z_2)}
\;=\; 0\,,
\]
which holds because the left side, viewed as a rational function of $z_1$
with $z_2, z_3$ fixed, has simple poles at $z_2$ and $z_3$ whose residues
sum to zero, hence vanishes.  Arnold proved that
\eqref{eq:preface-arnold}, replicated across all triples
$\{i,j,k\} \subset \{1, \ldots, n\}$, generates the \emph{complete} ideal
of relations in $H^*(\mathrm{Conf}_n(\mathbf{C}), \mathbf{C})$.

Under a coordinate change $z \mapsto w(z)$, the propagator transforms as
$\eta_{ij} \mapsto \eta_{ij} + d\log\frac{w(z_i) - w(z_j)}{z_i - z_j}$.
Near the diagonal this becomes $d\log w'(z_i)$: the standard cocycle for
$\mathrm{Diff}(X)$.  The propagator is a BRST ghost for diffeomorphisms,
a consequence of the form of~$\eta$.

\subsection*{Chiral algebras on a curve}

Let $X$ be a smooth algebraic curve over~$\mathbb C$.  Write
$\mathcal D_X$ for the sheaf of differential operators on~$X$; a
$\mathcal D_X$-module is a sheaf on which $\mathcal D_X$ acts,
equivalently a sheaf with a flat connection.
A \emph{chiral algebra}~$\cA$ on~$X$ is a $\mathcal D_X$-module
equipped with a \emph{chiral bracket}
\[
\mu^{\mathrm{ch}}
\;\colon\;
j_*j^*(\cA\boxtimes\cA)
\;\longrightarrow\;
\Delta_!(\cA),
\]
where $j\colon X\times X\setminus\Delta
\hookrightarrow X\times X$ is the inclusion of the
complement of the diagonal and
$\Delta_!\cA$ is the $!$-pushforward along the diagonal
embedding $\Delta\colon X\hookrightarrow X\times X$
(the $\mathcal{D}$-module direct image; concretely,
$\Delta_!\cA \cong \cA \otimes \delta_\Delta$, sections
of~$\cA$ supported on the diagonal via the
$\delta$-function).  The source
$j_*j^*(\cA\boxtimes\cA)$ is the $\mathcal{D}$-module
of sections of the external product
$\cA \boxtimes \cA$ with poles of arbitrary order
along~$\Delta$; the chiral bracket extracts the
singular part and projects it onto the diagonal.

In local coordinates, the chiral bracket encodes the \emph{operator
product expansion}: for sections~$a,b\in\cA$,
\[
a(z)\,b(w)
\;\sim\;
\sum_{n\ge 0}\frac{a_{(n)}b(w)}{(z-w)^{n+1}}\,.
\]
The $n$-th products $a_{(n)}b\in\cA$ are the
\emph{Fourier modes} of the bracket, extracted by the
residue formula
$a_{(n)}b = \operatorname{Res}_{z=w}
[a(z)\,b(w)\,(z{-}w)^n]$.
The zeroth product $a_{(0)}b$ is the Lie-type
bracket (first-order pole); the first product $a_{(1)}b$
contributes the second-order pole, carrying the
symmetric/metric data.  All higher products ($n\ge 2$)
are determined by the $\mathcal D_X$-module structure,
i.e.\ by translation covariance.

The \emph{Borcherds identity} couples all pole orders into a single
algebraic constraint:
\[
\boxed{
\sum_{j\ge 0}\binom{m}{j}(a_{(n+j)}b)_{(m+k-j)}c
\;=\;
\sum_{j\ge 0}(-1)^j\binom{n}{j}
\Bigl(
a_{(m+n-j)}(b_{(k+j)}c)
-(-1)^n b_{(n+k-j)}(a_{(m+j)}c)
\Bigr).
}
\]
At $n=0$: the Jacobi identity for the Lie bracket~$a_{(0)}$.
At $m=0$: the commutator formula.  At $n=1$, $m=k=0$:
the derivation property of $a_{(0)}$ with respect to $a_{(1)}b$.
The identity is simultaneously the locality axiom, the Jacobi
identity, and the associativity constraint.  A chiral algebra is a
$\mathcal D_X$-module whose $n$-th products satisfy the Borcherds
identity; conversely, the Borcherds identity is the complete set
of axioms.

\subsection*{The bar complex on~$X$}

Place sections $a_1,\dots,a_n\in\cA$ at distinct points
$z_1,\dots,z_n\in X$.  Assign to each ordered pair $(i,j)$ the
logarithmic $1$-form
\[
\eta_{ij}
\;:=\;
d\log(z_i-z_j)
\;=\;
\frac{dz_i-dz_j}{z_i-z_j}\,.
\]
For a spanning tree~$T$ of the complete graph on $\{1,\dots,n\}$, with edge set~$E(T)$,
form the decorated tensor
\[
\omega_T(a_1,\dots,a_n)
\;:=\;
a_1(z_1)\otimes\cdots\otimes a_n(z_n)
\;\otimes\;
\bigwedge_{(i,j)\in E(T)}\eta_{ij}\,.
\]
The form $\bigwedge_{(i,j)\in E(T)}\eta_{ij}$ is a section of
$\Omega^{n-1}_{\log}$ on the configuration space
$\mathrm{Conf}_n(X)$; its degree is~$|E(T)|=n-1$ since~$T$ is a
tree.

The Fulton--MacPherson compactification
$\overline{\mathrm{FM}}_n(X)$ resolves $\mathrm{Conf}_n(X)$ by
iterated real oriented blowup along all diagonal strata.  This is a
\emph{blowup}, not the complement of the diagonal: points of
$\overline{\mathrm{FM}}_n(X)\setminus\mathrm{Conf}_n(X)$ record
the limiting direction, rate, and relative scales of approach as
points collide.  The boundary is a manifold with corners; the
codimension-one faces are indexed by subsets $S\subseteq\{1,\dots,n\}$
with $|S|\ge 2$, recording which points have collided.

The \emph{chiral bar complex} on~$X$:
\[
\barB_X(\cA)
\;=\;
\bigoplus_{n\ge 1}
\bigl(s^{-1}\bar\cA\bigr)^{\otimes n}_{\Sigma_n}
\;\otimes\;
\Gamma\bigl(\overline{\mathrm{FM}}_n(X),\;
\Omega^{n-1}_{\log}\bigr).
\]
Here $\bar\cA = \ker(\varepsilon\colon\cA\to\omega_X)$ is the
augmentation ideal (the kernel of the vacuum map), and
$s^{-1}$ denotes \emph{desuspension}: the shift
$|s^{-1}a| = |a| - 1$ in cohomological degree.  Throughout this
monograph, cohomological conventions are used: $|d| = +1$.
This is a graded coalgebra: the \emph{deconcatenation coproduct}
\[
\Delta[s^{-1}a_1|\cdots|s^{-1}a_n]
\;=\;
\sum_{i=0}^{n}
[s^{-1}a_1|\cdots|s^{-1}a_i]
\;\otimes\;
[s^{-1}a_{i+1}|\cdots|s^{-1}a_n]
\]
splits an ordered sequence at every position.  It is equipped with
a differential $d_{\barB}$ that decomposes into three pieces:
\[
d_{\barB}
\;=\;
d_{\mathrm{int}}+d_{\mathrm{res}}+d_{\mathrm{dR}}\,.
\]
The three components:
\begin{itemize}
\item $d_{\mathrm{int}}$: the internal differential of~$\cA$
(the translation operator, acting on each tensor factor).
\item $d_{\mathrm{res}}$: the \emph{residue differential}. For
a codimension-one boundary face $D_S$ of
$\overline{\mathrm{FM}}_n(X)$ corresponding to the collision
$\{z_i\}_{i\in S}\to z_0$, the residue along~$D_S$ extracts
the OPE coefficient: the iterated contraction
$a_{i_1(n_1)}(a_{i_2(n_2)}(\cdots))$ at the pole orders
dictated by the form $\bigwedge\eta_{ij}$.  In formulas: for
$S=\{i,j\}$,
\[
d_{\mathrm{res}}^{(ij)}
\bigl(
a_1\otimes\cdots\otimes a_n\otimes\eta_{ij}\wedge\omega'
\bigr)
\;=\;
\pm\,
a_1\otimes\cdots\otimes
\widehat{a_i}\otimes\cdots\otimes
\widehat{a_j}\otimes\cdots\otimes
a_{i(p)}a_j
\;\otimes\;
\omega',
\]
where $p$ is the pole order read from the form-theoretic
coefficient, and hats denote omission.
\item $d_{\mathrm{dR}}$: the de~Rham differential on the
logarithmic forms on~$\overline{\mathrm{FM}}_n(X)$.
\end{itemize}

Does $d_{\barB}^2 = 0$?

\subsection*{The proof that $d_{\barB}^2=0$}

Expand $(d_{\mathrm{int}}+d_{\mathrm{res}}+d_{\mathrm{dR}})^2$
into nine terms.  The diagonal terms: $d_{\mathrm{int}}^2=0$
(since~$\cA$ is a cochain complex), $d_{\mathrm{dR}}^2=0$
(de~Rham), and $d_{\mathrm{res}}^2$ must be controlled.  The
cross-terms $d_{\mathrm{int}}\,d_{\mathrm{dR}}+
d_{\mathrm{dR}}\,d_{\mathrm{int}}=0$ by
the Leibniz rule.  The remaining five terms pair into three
cancellation mechanisms, governed by the combinatorics of index
overlap:
\begin{enumerate}[label=(\alph*)]
\item \emph{Disjoint supports.}\; When $\{i,j\}\cap\{k,l\}
=\emptyset$, the boundary faces~$D_{\{i,j\}}$
and~$D_{\{k,l\}}$ are transverse in
$\overline{\mathrm{FM}}_n(X)$.  The corresponding residue
operators commute, so the cross-terms cancel:
$d_{\mathrm{res}}^{(ij)}\,d_{\mathrm{res}}^{(kl)}
+d_{\mathrm{res}}^{(kl)}\,d_{\mathrm{res}}^{(ij)}=0$.
This is the operadic associativity of disjoint contractions.
\item \emph{Shared index.}\; When
$\{i,j\}\cap\{k,l\}=\{j=k\}$, the triple collision
$z_i=z_j=z_l$ lies in a codimension-two stratum.  The
form-theoretic contribution involves
$\eta_{ij}\wedge\eta_{jl}$.  The \emph{Arnold relation}
\[
\eta_{ij}\wedge\eta_{jl}
+\eta_{jl}\wedge\eta_{li}
+\eta_{li}\wedge\eta_{ij}
\;=\;0
\]
identifies this with a cyclic sum over the three ordered
approaches to the triple-collision point.  On the algebraic
side, the three terms produce
$(a_{i(m)}a_j)_{(n)}a_l$, $(a_{j(m)}a_l)_{(n)}a_i$,
$(a_{l(m)}a_i)_{(n)}a_j$ (with appropriate pole orders),
whose sum vanishes by the Borcherds identity.  The Arnold
relation kills the form; the Borcherds identity kills the
algebra.  Neither alone suffices; both are needed, and both
are consumed without remainder.
\item \emph{Same pair.}\;
$d_{\mathrm{res}}^{(ij)}\,d_{\mathrm{res}}^{(ij)}=0$ by the
sign rule on desuspensions: extracting a residue twice at the
same diagonal is zero for degree reasons.
\end{enumerate}

The result: $d_{\barB}^2=0$ if and only if the $n$-th products
satisfy the Borcherds identity.  The bar construction accepts
exactly chiral algebras.

This is genus~$0$.  At genus~$g \geq 1$, the propagator acquires
quasi-periodicity corrections and $d_{\mathrm{fib}}^{\,2} \neq 0$:
the curvature $d_{\mathrm{fib}}^{\,2} = \kappa(\cA) \cdot \omega_g$
produces a scalar $\kappa(\cA)$ that controls the entire genus
expansion.  The bar complex at genus~$0$ is uncurved algebra;
at genus~$\geq 1$ it becomes gravitational geometry.

\subsection*{The categorical logarithm}

The bar construction is a categorical logarithm.  The fundamental
property of $\log$, that $\log(ab)=\log a+\log b$, becomes:
\[
B(\cA\otimes\cA')
\;\simeq\;
B(\cA)\oplus B(\cA').
\]
The bar functor sends tensor products to direct sums.  The
logarithmic form $\eta_{ij}=d\log(z_i-z_j)$ is its integral
kernel.  The Arnold relation
\[
\eta_{ij}\wedge\eta_{jk}
+\eta_{jk}\wedge\eta_{ki}
+\eta_{ki}\wedge\eta_{ij}
\;=\;0
\]
is the cocycle condition for $\log$: the three-term identity states
that $d\log$ takes values in a commutative algebra ($1$-forms on
configuration space satisfy the Arnold algebra relations), so that
the logarithm is well-defined on products.

The cobar functor $\Omega(\barB(\cA))$ is the exponential.  The
domain on which the exponential inverts the logarithm, the
\emph{radius of convergence}, is the Koszul locus: the full
subcategory of chiral algebras for which
\[
\varepsilon\colon\Omega(\barB(\cA))
\;\xrightarrow{\;\sim\;}\;
\cA.
\]
Outside the Koszul locus, the cobar-bar resolution still exists as
a free resolution, but it is infinite, carrying higher homotopies
that measure the failure of the exponential to converge.

The cobar functor recovers the original algebra~$\cA$ from its
bar complex.  A different operation, linear duality of bar cohomology,
produces a genuinely new algebra: the Koszul dual~$\cA^!$.

\subsection*{Two duals of the bar complex}

The \emph{Koszul dual algebra}~$\cA^!$ is obtained by a two-step
algebraic procedure.  First, take bar cohomology:
\[
\cA^{\mathrm i}
\;:=\;
H^*\bigl(B(\cA)\bigr),
\]
a graded coalgebra (the coproduct of $B(\cA)$ descends to
cohomology).  Second, apply graded linear duality:
\[
\cA^!
\;:=\;
\bigl(\cA^{\mathrm i}\bigr)^\vee.
\]
This is the Koszul dual algebra, not the cobar.  The distinction is
essential: $\Omega(B(\cA))\simeq\cA$ is bar-cobar \emph{inversion},
recovering the original algebra; $\cA^!$ is obtained by
\emph{linear duality of bar cohomology}, producing a genuinely
different algebra except in the self-dual case.

A separate, geometric operation also acts on the bar coalgebra:
Verdier duality on $\mathrm{Ran}(X)$ sends $\barB_X(\cA)$ to the
\emph{homotopy} Koszul dual~$\cA^!_\infty$:
\[
\mathbb D_{\mathrm{Ran}}\,\barB_X(\cA)
\;\simeq\;
\cA^!_\infty.
\]
This is a factorization \emph{algebra}, not a coalgebra --- Verdier
duality converts the coalgebra structure of~$\barB_X(\cA)$
into an algebra structure.  The homotopy dual~$\cA^!_\infty$ is a
richer object than~$\cA^!$: it retains the full chain-level data of
the bar complex, while~$\cA^!$ remembers only the cohomology.  That
the two are compatible (that the cohomology of
$\cA^!_\infty$ recovers~$\cA^!$ on the Koszul locus) is the
content of Theorem~A (the Verdier intertwining theorem), not a
tautology.

When~$\cA$ is chirally Koszul, $B(\cA)$ has cohomology concentrated
in a single row, $\cA^{\mathrm i}$ is a coalgebra with a unique
grading, and $\cA^!$ governs a linear (quadratic) resolution
of~$\cA$.  The bar-to-cobar spectral sequence collapses at~$E_2$.
Classical Koszul duality
(Priddy, Beilinson--Ginzburg--Soergel, Loday--Vallette) is
recovered on $X=\mathbb A^1$: the affine line is contractible,
so $\overline{C}_n(\mathbb A^1)$ deformation-retracts onto
a point, the FM chain cooperad becomes quasi-isomorphic to the
associative cooperad, and the bar construction reduces to the
classical bar complex of the underlying Lie algebra.

The Koszul dual~$\cA^!$ arises from the holomorphic
(symmetric) bar complex.  But the bar construction also has a
topological (ordered) wing, producing a second Koszul dual.

\subsection*{Two Koszul dualities}

The bar complex of a chiral algebra~$\cA$ carries two operadic
colours, and each colour has its own Koszul duality.  The
\emph{closed colour}~(holomorphic) uses the symmetric bar
complex~$\barB^{\Sigma}(\cA)$, built on the Fulton--MacPherson
compactification $\overline{\operatorname{FM}}_n(\mathbb C)$
with~$\Sigma_n$-coinvariants.  Its Koszul dual~$\cA^!_{\mathrm{ch}}$
is the chiral Koszul dual described above: the Francis--Gaitsgory
construction via Verdier duality on~$\operatorname{Ran}(X)$.

The \emph{open colour}~(topological) uses the ordered bar
complex~$\barB^{\mathrm{ord}}(\cA)$, built on ordered
configurations~$\operatorname{Conf}_n^{\mathrm{ord}}(\mathbb C)
\times\operatorname{Conf}_n(\mathbb R)$ with \emph{no}
$\Sigma_n$-quotient: the linear ordering on~$\mathbb R$ is
retained.  Its Koszul dual~$\cA^!_{\mathrm{line}}$ governs the
category of line operators: when~$\cA$ is affine Kac--Moody,
$\cA^!_{\mathrm{line}}$ is the Yangian~$Y(\mathfrak g)$
(the quantum group that deforms the enveloping algebra
$U(\mathfrak g[z])$ of polynomial currents).

The two bar complexes are related by a descent map
$\barB^{\mathrm{ord}}(\cA)\to\barB^{\Sigma}(\cA)$ that takes
$\Sigma_n$-coinvariants.  For a chiral algebra with OPE poles,
this descent is \emph{not} naive: it requires the spectral
$R$-matrix $R(z)$ as twisting datum.  The $R$-matrix is the
cross-colour data connecting the two wings of Koszul duality.
It is derived from the local OPE for vertex algebras
($E_\infty$-chiral), and is independent input for nonlocal
quantum vertex algebras ($E_1$-chiral, in the sense of
Etingof--Kazhdan).

\subsection*{The Heisenberg atom}

The Heisenberg chiral algebra $\mathcal H_k$ is generated by a
single field~$\alpha$ of conformal weight~$1$ with OPE
\[
\alpha(z)\,\alpha(w)
\;\sim\;
\frac{k}{(z-w)^2}\,.
\]
Only the first product is nonzero: $\alpha_{(1)}\alpha=k\cdot\mathbf 1$
and $\alpha_{(n)}\alpha=0$ for $n\neq 1$.  No first-order pole:
$\alpha_{(0)}\alpha=0$.  The Borcherds identity is satisfied
trivially: all triple products vanish since the only nontrivial
product is $\alpha_{(1)}\alpha\in\Bbbk\cdot\mathbf 1$, and
$\mathbf 1_{(n)}=0$ for $n\ge 0$.

The bar complex at tensor degree~$n$:
\[
\barB^n_X(\mathcal H_k)
\;=\;
(s^{-1}\alpha)^{\otimes n}_{\Sigma_n}
\;\otimes\;
\Gamma\bigl(\overline{\mathrm{FM}}_n(X),\;
\Omega^{n-1}_{\log}\bigr).
\]
\emph{Tensor degree~$1$}: the space is $s^{-1}\alpha$, one-dimensional,
with $d_{\barB}=d_{\mathrm{int}}=0$.

\emph{Tensor degree~$2$}: the bar component is
$(s^{-1}\alpha)^{\otimes 2}\otimes\langle\eta_{12}\rangle$.
The bar differential extracts the full chiral product:
$d_{\mathrm{res}}(s^{-1}\alpha\otimes s^{-1}\alpha
\otimes\eta_{12}) = \alpha_{(1)}\alpha = k\cdot\mathbf{1}$.
The double-pole mode is extracted by
$d_{\mathrm{curvature}}$
(Proposition~\ref{prop:pole-decomposition}); since
$\alpha_{(0)}\alpha = 0$, the bracket component vanishes.
The level~$k$ is visible already at genus~$0$; at genus~$1$
the curvature acquires a topological component
$d_{\mathrm{fib}}^2 = \kappa(\cH_k)\cdot\omega_1$
(Example~\ref{ex:heisenberg-d-deg1}).

\emph{Tensor degree~$n\ge 3$}: every residue at a codimension-one
collision stratum $D_{\{i,j\}}$ extracts $\alpha_{(1)}\alpha
=k\cdot\mathbf 1$ on the pair $(i,j)$.  The remaining $n-2$
factors are~$\alpha$; since $\mathbf 1_{(p)}\alpha=0$ for
$p\ge 0$, no further contractions occur.  All structure is
captured at tensor degree~$2$: the bar complex is
\emph{quadratic}.  The Heisenberg algebra is chirally Koszul.

The modular characteristic:
\[
\kappa(\mathcal H_k)\;=\;k.
\]
The Koszul dual is the \emph{curved} symmetric chiral algebra
\[
\mathcal H_k^!
\;=\;
\bigl(\mathrm{Sym}^{\mathrm{ch}}(V^*),\;m_0=-k\omega\bigr),
\]
where $V^*$ is the $\Bbbk$-linear dual of the generating space and
$m_0=-k\omega$ is the curvature: a degree-$2$ element satisfying
the curved $A_\infty$ relation
\[
m_1^{\,2}(a)\;=\;[m_0,a]
\]
(commutator, with the minus sign).  The differential $m_1$ does not
square to zero; its failure is controlled by the curvature.  The
curvature~$m_0$ is the bar-dual of the OPE coefficient~$k$:
the algebra side has a scalar OPE; the dual side has a scalar
curvature.

The Heisenberg has only a second-order pole: the bar complex is
quadratic.  The first example with both first- and second-order
poles is the affine Kac--Moody algebra.

\subsection*{The Kac--Moody OPE}

The affine Kac--Moody algebra $\widehat{\mathfrak g}_k$ at level~$k$
is generated by currents $J^a$, $a=1,\dots,\dim\mathfrak g$, with
OPE
\[
J^a(z)\,J^b(w)
\;\sim\;
\frac{f^{ab}{}_{c}\,J^c(w)}{z-w}
\;+\;
\frac{k\,\kappa^{ab}}{(z-w)^2}\,,
\]
where $f^{ab}{}_{c}$ are the structure constants of the simple Lie
algebra~$\mathfrak g$ and $\kappa^{ab}$ is the Killing form
normalised so that long roots have squared length~$2$.  Both poles
are present: the first-order pole carries the Lie bracket
$J^a_{(0)}J^b=f^{ab}{}_{c}J^c$; the second-order pole carries
the invariant inner product
$J^a_{(1)}J^b=k\,\kappa^{ab}\cdot\mathbf 1$.  The bar complex
of $\widehat{\mathfrak g}_k$ therefore has nontrivial contributions
at all tensor degrees: the first-order pole generates structure
constants at tensor degree~$n$ from tree-level OPE contractions,
and the second-order pole contributes the metric/curvature data.

The bracket and curvature decomposition:
\[
\mu^{\mathrm{ch}}
\;=\;
\underbrace{f^{ab}{}_{c}\,J^c\cdot\eta_{12}}_{\text{Lie bracket
(first-order pole)}}
\;+\;
\underbrace{k\,\kappa^{ab}\cdot\mathbf 1\cdot
d\eta_{12}}_{\text{inner product (second-order pole)}}.
\]
The Lie bracket contributes the tree-level bar differential
(combinatorics of the Chevalley--Eilenberg complex); the inner
product contributes the curvature~$\kappa$.  The coexistence of
both poles, absent in the pure second-order-pole Heisenberg case,
makes $\widehat{\mathfrak g}_k$ the first nontrivial example.


\begin{remark}[The zero-dimensional shadow]\label{rem:preface-zero-dim}
When $X=\operatorname{Spec}\Bbbk$ is a point, configuration spaces
collapse, logarithmic forms vanish, and the chiral bar complex
recovers the classical bar construction of an associative
algebra~$A$.  A \emph{quadratic algebra} $A=T(V)/(R)$ has quadratic
dual $A^!=T(V^*)/(R^\perp)$; when~$A$ is Koszul, the bar
cohomology concentrates in diagonal degrees and
$H^*(B(A))\cong(A^!)^\vee$.  The operadic instances
$\mathrm{Com}^!=\mathrm{Lie}$ and $\mathrm{Sym}^!=\Lambda$ recover
the Chevalley--Eilenberg complex as a restricted bar construction.
When Koszulness fails, the cobar-bar resolution
$\Omega(B(A))\xrightarrow{\sim}A$ is the universal replacement.
\end{remark}

Everything above takes place at genus~$0$: the propagator
$\eta_{12}=d\log(z_1-z_2)$ is globally defined on~$\mathbb P^1$,
and the Arnold relation holds without correction.  On a curve of
genus~$g \geq 1$, the function $z_1 - z_2$ has no global meaning:
the curve is compact, and any meromorphic function with a single
simple zero must also have a simple pole.  The Arnold relation
acquires a defect, the bar differential no longer squares to zero,
and the defect is controlled by a single scalar.


% ====================================================================
\section*{2.\quad Curvature and the genus tower}
% ====================================================================

\subsection*{The genus-$g$ propagator}

At genus $g\ge 1$, the difference $z_1-z_2$ has no global meaning.
The replacement is the \emph{prime form} $E(z_1,z_2)$: a section
of $K^{-1/2}\boxtimes K^{-1/2}$ on $X\times X$, vanishing to
first order along the diagonal $\Delta$, with no other zeros.  The
bundle is $K^{-1/2}\boxtimes K^{-1/2}$, \emph{not}
$K^{+1/2}\boxtimes K^{+1/2}$: the prime form is a
$(-\frac12,-\frac12)$-differential.  In a local coordinate where
the diagonal is $z_1=z_2$,
\[
E(z_1,z_2)
\;=\;
(z_1-z_2)\cdot\bigl(1+O(z_1-z_2)\bigr)
\cdot(dz_1)^{-1/2}(dz_2)^{-1/2}.
\]

The prime form has nontrivial monodromy.  Analytic continuation
around the $B$-cycle $B_j$ in the variable~$z_1$:
\[
E(z_1+B_j,z_2)
\;=\;
-\exp\bigl(
-\pi i\Omega_{jj}-2\pi i\textstyle\int_{z_2}^{z_1}\omega_j
\bigr)
\cdot E(z_1,z_2),
\]
where $\Omega=(\Omega_{jk})$ is the period matrix of~$X$
($\Omega_{jk}=\oint_{B_k}\omega_j$) and
$\omega_1,\dots,\omega_g$ are the holomorphic differentials
normalised by $\oint_{A_j}\omega_k=\delta_{jk}$.  The
$A$-cycle monodromy is trivial: $E(z_1+A_j,z_2)=E(z_1,z_2)$.

The logarithmic derivative
\[
\omega(z_1,z_2)
\;:=\;
d_{z_1}\log E(z_1,z_2)
\]
is the fundamental meromorphic differential of the second kind:
symmetric, a double pole on~$\Delta$, vanishing $A$-periods.  The
\emph{genus-$g$ propagator}:
\[
\eta^{(g)}_{12}
\;=\;
d\log E(z_1,z_2)
\;+\;
\pi\sum_{j,k=1}^{g}
(\mathrm{Im}\,\Omega)^{-1}_{jk}\,
\mathrm{Im}\!\Bigl(\int_{z_2}^{z_1}\omega_j\Bigr)\,
\omega_k(z_1).
\]
The period correction $(\mathrm{Im}\,\Omega)^{-1}_{jk}$
compensates the $B$-cycle monodromy, rendering $\eta^{(g)}_{12}$
single-valued on~$X$.  The price: $\eta^{(g)}_{12}$ is no longer
holomorphic: the correction term is a $(1,0)$-form in~$z_1$
multiplied by a real-analytic function of both variables.  The
propagator couples to the Hodge bundle
$\mathbb E\to\overline{\mathcal M}_g$ through the period
matrix~$\Omega$.

\subsection*{Curvature}

The Arnold relation at genus~$g$ acquires a defect.  At genus~$0$,
\[
\eta_{12}\wedge\eta_{23}
+\eta_{23}\wedge\eta_{31}
+\eta_{31}\wedge\eta_{12}
\;=\;0
\]
holds identically.  At genus $g\ge 1$, the period corrections
produce a residual $(1,1)$-form: the three-term sum does not vanish.
The fibrewise bar differential satisfies
\begin{equation}\label{eq:pref-curvature}
d_{\mathrm{fib}}^{\,2}\;=\;\kappa(\cA)\cdot\omega_g,
\end{equation}
where $\omega_g$ is the Arakelov $(1,1)$-form on the fibre of the
universal curve $\pi\colon\mathcal C_g\to\overline{\mathcal M}_g$
(the family of genus-$g$ curves parametrised by the
Deligne--Mumford moduli space $\overline{\mathcal M}_g$),
and $\kappa(\cA)\in\Bbbk$ is the scalar \emph{modular
characteristic}, determined entirely by the leading OPE singularity.

For the Heisenberg algebra: the only OPE datum entering the bar
differential is $\alpha_{(1)}\alpha=k$.  Every residue at a
codimension-one collision stratum extracts this coefficient.  The
defect of the Arnold relation at genus~$g$ is
\[
d_{\mathrm{fib}}^{\,2}\big|_{\mathcal H_k}
\;=\;
k\cdot\omega_g,
\qquad\text{so}\quad
\kappa(\mathcal H_k)=k.
\]
For the Kac--Moody algebra: the bracket
$J^a_{(0)}J^b=f^{ab}{}_{c}J^c$ and the inner product
$J^a_{(1)}J^b=k\kappa^{ab}$ both contribute.  The curvature
receives the trace over the adjoint representation:
\[
\kappa(\widehat{\mathfrak g}_k)
\;=\;
\frac{(k+h^\vee)\dim\mathfrak g}{2h^\vee}\,.
\]
The numerator $k+h^\vee$ is the \emph{shifted level}; $h^\vee$ is
the dual Coxeter number.  At $k=-h^\vee$ (the critical level),
$\kappa=0$ and the bar complex is \emph{uncurved}: the Sugawara
construction is undefined (the central charge
$c=k\dim\mathfrak g/(k+h^\vee)$ has a pole), but the curvature
parameter vanishes.

For the Virasoro algebra at central charge~$c$: the stress tensor
$T$ has OPE $T(z)T(w)\sim\frac{c/2}{(z-w)^4}
+\frac{2T(w)}{(z-w)^2}+\frac{\partial T(w)}{z-w}$.
The bar propagator $d\log E(z,w)$ absorbs one pole order
(the $d\log$ measure sends $z^{-n}$ to $z^{-(n-1)}$), so the
collision residue $r(z)=(c/2)/z^3+2T/z$ has pole orders one
less than the OPE.  The curvature computation gives
\[
\kappa(\mathrm{Vir}_c)\;=\;\frac{c}{2}\,.
\]
The Koszul dual is $\mathrm{Vir}_{26-c}$, with
$\kappa(\mathrm{Vir}_{26-c})=(26-c)/2$: the two curvatures
sum to~$13$, not zero.  At $c=26$ the dual is uncurved; at
$c=0$ the algebra itself is uncurved; at $c=13$ the algebra
is self-dual under Koszul duality.

\subsection*{Period integrals restore nilpotence}

The curvature~\eqref{eq:pref-curvature} obstructs
$d_{\mathrm{fib}}^2=0$, but not the total $D_g^2=0$.
Integration against $A$-cycle periods defines a connection on the
family of bar complexes parameterised by~$\overline{\mathcal M}_g$.
The corrected total differential
\[
D_g\;=\;d_{\mathrm{fib}}+\nabla^{\mathrm{GM}}
\]
incorporates the Gauss--Manin connection (the canonical flat
connection on the cohomology bundle $R^1\pi_*\mathbb C$ of
the universal family, encoding how the periods of the curve vary
with moduli) on the Hodge bundle, and
$D_g^{\,2}=0$: the $(1,1)$-curvature of the fibrewise differential
is absorbed by the $(0,1)$-part of the base connection.

The mechanism: the fibrewise curvature $\kappa\cdot\omega_g$ is a
class in $H^{1,1}(\mathcal C_g)$; the period map
$\overline{\mathcal M}_g\to\mathcal A_g$ (to the moduli of abelian
varieties) identifies this class with the $(0,1)$-curvature of the
Gauss--Manin connection on $R^1\pi_*\mathbb C$.  The two
curvatures cancel:
\[
D_g^{\,2}
\;=\;
d_{\mathrm{fib}}^2
+[d_{\mathrm{fib}},\nabla^{\mathrm{GM}}]
+(\nabla^{\mathrm{GM}})^2
\;=\;
\kappa\cdot\omega_g-\kappa\cdot\omega_g+0
\;=\;0.
\]

\subsection*{The genus tower}

The bar complex traces a family of curved cochain complexes over
$\overline{\mathcal M}_g$.  For uniform-weight algebras
(single-generator, or multi-generator with all generators of the
same conformal weight), the obstruction to flatness at
genus~$g$ is the characteristic class
\[
\mathrm{obs}_g(\cA)
\;=\;
\kappa(\cA)\cdot\lambda_g
\;\in\;
H^*(\overline{\mathcal M}_g),
\qquad
\lambda_g\;=\;c_g(\mathbb E),
\]
where $\mathbb E = \pi_*\omega_\pi$ is the \emph{Hodge bundle}:
the vector bundle on $\overline{\mathcal M}_g$ whose fibre over a
point $[C]$ is the $g$-dimensional space
$H^0(C, \omega_C)$ of holomorphic differentials on~$C$.
At genus~$1$ this
factorization holds unconditionally for all families; for
multi-weight families at genus~$g \geq 2$ the factorization
remains open
\textup{(}see \S\textup{\ref{sec:modular-char-spectral-disc-intro}}\textup{)}.  Grothendieck--Riemann--Roch
applied to the universal curve
$\pi\colon\mathcal C_g\to\overline{\mathcal M}_g$ computes the
total obstruction: the Chern character of $R\pi_*\omega_\pi$
involves the Todd class of the relative tangent bundle~$T_\pi$,
which is the $\hat A$-genus.  The generating function:
\[
\sum_{g\ge 1}\mathrm{obs}_g(\cA)\cdot x^{2g}
\;=\;
\kappa(\cA)\cdot\bigl(\hat A(ix)-1\bigr).
\]
Since $\hat A(ix)=(x/2)/\sin(x/2)
=1+x^2/24+7x^4/5760+\cdots$ (all positive),
the first Faber--Pandharipande coefficients are:
\begin{align*}
F_1(\cA)
&\;=\;
\frac{\kappa(\cA)}{24}\,,\\[3pt]
F_2(\cA)
&\;=\;
\frac{7\,\kappa(\cA)}{5760}\,,\\[3pt]
F_3(\cA)
&\;=\;
\frac{31\,\kappa(\cA)}{967680}\,.
\end{align*}
The genus-$g$ coefficient is
$\kappa(\cA)\cdot\tfrac{2^{2g-1}-1}{2^{2g-1}}
\cdot\tfrac{|B_{2g}|}{(2g)!}$
(the Faber--Pandharipande $\lambda_g$-integral).  The
$\hat A$-genus appears from the bar complex as the connection between chiral
algebra and index theory.

The scalar $\kappa(\cA)$ is only the leading term.  The bar complex
carries higher-arity data: a universal Maurer--Cartan element
$\Theta_\cA$ whose projection to arity~$r$ yields a shadow invariant
$S_r(\cA)$.  On each primary deformation line~$L$, the shadow
generating function $H(t)=\sum_{r\ge 2}rS_r\,t^r$ satisfies the
algebraic relation
\begin{equation}\label{eq:preface-riccati-hook}
H(t)^2 \;=\; t^4\,Q_L(t),
\qquad
Q_L(t) = 4\kappa^2+12\kappa\alpha\,t+(9\alpha^2+16\kappa S_4)\,t^2,
\end{equation}
a quadratic polynomial in three genus-$0$ invariants
$(\kappa,\alpha,S_4)$
(Theorem~\ref{thm:riccati-algebraicity}).  The infinite tower is
algebraic of degree~$2$: determined, computable, and governed by the
single discriminant $\Delta = 8\kappa S_4$.

\subsection*{Complementarity}

Verdier duality on the Ran space splits the center local system
into two halves, one controlled by~$\cA$ and one by~$\cA^!$.
The splitting carries a shifted-symplectic structure.
The complementary summands:
\[
R\Gamma(\overline{\mathcal M}_g,\;\mathcal Z_\cA)
\;\simeq\;
\mathbf Q_g(\cA)\;\oplus\;\mathbf Q_g(\cA^!).
\]
What~$\cA$ sees as deformation, $\cA^!$ sees as obstruction.
The natural pairing
\[
\mathbf Q_g(\cA)\otimes\mathbf Q_g(\cA^!)
\;\longrightarrow\;
R\Gamma(\overline{\mathcal M}_g,\;\omega_{\overline{\mathcal M}_g})
\;\simeq\;\Bbbk[-(3g-3)]
\]
is a $(-(3g-3))$-shifted symplectic form, and the two summands are
\emph{Lagrangian}: each is isotropic and of half the total
dimension.  At the scalar level, complementarity reduces to
\[
\kappa(\cA)+\kappa(\cA^!)\;=\;0
\qquad\text{(for Kac--Moody and free-field algebras).}
\]
For $\mathcal{W}$-algebras the sum $\kappa+\kappa^!$ is a nonzero
constant: $13$ for Virasoro, $250/3$ for~$\mathcal{W}_3$.

\subsection*{Feigin--Frenkel duality}

The Sugawara construction produces the Virasoro field
\[
T(z)
\;=\;
\frac{1}{2(k+h^\vee)}\sum_{a=1}^{\dim\mathfrak g}
{:}J^a(z)J^a(z){:}\,,
\]
with central charge $c=k\dim\mathfrak g/(k+h^\vee)$.  At the
critical level $k=-h^\vee$, the denominator vanishes: $T(z)$ is
\emph{undefined}, not ``$c$ diverges.''  The chiral algebra
acquires a large center, the Feigin--Frenkel center
$\mathfrak z(\widehat{\mathfrak g}_{-h^\vee})$, isomorphic to the
algebra of functions on the space of local ${}^L\mathfrak g$-opers
on the formal disc.

The Feigin--Frenkel involution
\[
k\;\longleftrightarrow\;-k-2h^\vee
\]
is Koszul duality on configuration spaces: it interchanges~$\cA$
and~$\cA^!$ while preserving the bar-cobar adjunction.  At the
level of modular characteristics,
$\kappa(\widehat{\mathfrak g}_k)+
\kappa(\widehat{\mathfrak g}_{-k-2h^\vee})=0$:
complementarity is a direct consequence.  At the critical
level, the Koszul dual is the Langlands-dual critical-level
algebra~$\widehat{{}^L\mathfrak g}_{-{}^Lh^\vee}$, not a
renormalised copy of the original.

\subsection*{The total space}

The universal configuration fibration
\[
\pi_n\colon
\overline{\mathcal C}_n(\mathcal C_g)
\;\longrightarrow\;
\overline{\mathcal M}_g
\]
packages the bar complex into a single global object.  Its boundary
divisors carry two distinct geometric roles:
\begin{itemize}
\item \emph{Collision divisors} (vertical): the fibrewise boundary
of $\overline{\mathrm{FM}}_n(X_s)$ over a point
$s\in\overline{\mathcal M}_g$.  These produce the bar
differential~$d_{\mathrm{res}}$, the OPE residues.
\item \emph{Degeneration divisors} (horizontal): the boundary of
$\overline{\mathcal M}_g$ itself (nodal curves, reducible
fibres).  These produce the period corrections, the
Gauss--Manin connection terms in~$D_g$.
\end{itemize}
The collision divisors are the ``algebraic'' boundary (controlled by
the Borcherds identity); the degeneration divisors are the
``geometric'' boundary (controlled by the period map and the
clutching morphisms of stable curves).  The interaction between them
is the curvature~$\kappa$: the fibrewise bar differential fails to
be nilpotent precisely because the vertical and horizontal
boundaries do not commute.

% ====================================================================
\section*{3.\quad Modular homotopy theory}
% ====================================================================

The genus tower demands an organising framework.  The
fibrewise differential~$d_{\mathrm{fib}}$, the Gauss--Manin
correction~$\nabla^{\mathrm{GM}}$, and the clutching morphisms at
boundary strata satisfy compatibility relations dictated by the
stratification of $\overline{\cM}_{g,n}$.  The algebraic structure
governing these compatibilities across all genera simultaneously
is the \emph{modular operad}: an operad whose operations
are indexed not by trees but by connected stable graphs of
arbitrary genus.

The \emph{modular homotopy type} of~$\cA$ is the formal moduli
problem controlling the inverse system of bar complexes
$\barB^{(g)}(\cA)$ over all genera:
\[
\mathcal M^{\mathrm{mod}}_\cA(R)
\;:=\;
\mathrm{MC}\!\bigl(
\mathfrak g^{\mathrm{mod}}_\cA \,\widehat\otimes_{\mathfrak m}\, R
\bigr)\big/{\sim}
\]
for local Artin rings~$R$.  Here
$\mathfrak g^{\mathrm{mod}}_\cA$ is the \emph{modular convolution algebra}: a complete filtered cyclic
$L_\infty$-algebra (a chain complex with multilinear brackets $\ell_1, \ell_2, \ell_3, \ldots$ satisfying
a hierarchy of Jacobi-type identities, generalising Lie algebras
to the homotopy-coherent setting).
Its construction requires three inputs: a homotopy chiral algebra on
the curve (the algebraic input), a cooperadic chain complex on
logarithmic configuration spaces (the geometric input), and a
convolution $L_\infty$-structure mediating between them (the
homotopical input).  The bar complex, the Koszul dual, the genus
tower, the complementarity splitting, the shadow obstruction tower,
and the holographic correspondence of Volume~II are all
representations of the formal group defined by $\mathcal M^{\mathrm{mod}}_\cA$.

The convolution algebra $\mathfrak g^{\mathrm{mod}}_\cA$ has a
canonical Maurer--Cartan element
$\Theta_\cA\in\mathrm{MC}(\mathfrak g^{\mathrm{mod}}_\cA)$
(section~4), a tangent complex governing its deformations
(section~5), and a Postnikov tower of finite-order
projections (section~6).

% --- Escalation: the three levels of structure ---

\subsection*{3.1.\enspace The modular operad}

At genus~$0$, the combinatorics of the bar complex is governed by
trees.  At higher genus, trees are replaced by stable graphs: graphs
with genus labels at their vertices, parametrising the boundary
strata of the Deligne--Mumford moduli space $\overline{\cM}_{g,n}$.

A \emph{modular operad}~$\cO$
(Getzler--Kapranov~\cite{GeK98}) has operations indexed
not by trees but by \emph{connected stable graphs} (graphs
of arbitrary genus).  A \emph{connected stable
graph}~$\Gamma$ has a genus label
$g(v)\in\mathbb Z_{\ge 0}$ at each vertex satisfying
$2g(v)-2+\mathrm{val}(v)>0$ (stability), and total genus
$g(\Gamma)=b_1(\Gamma)+\sum_v g(v)$; trees are the
genus-$0$ case.
The structure maps of~$\cO$ are of two kinds:
\emph{separating gluing}
$\xi_{\mathrm{sep}} \colon
\cO(g_1, n_1{+}1) \otimes \cO(g_2, n_2{+}1)
\to \cO(g_1{+}g_2, n_1{+}n_2)$
(joining two components at a node), and
\emph{non-separating gluing}
$\xi_{\mathrm{ns}} \colon \cO(g, n{+}2)
\to \cO(g{+}1, n)$
(identifying two marked points on the same component,
raising genus by~$1$).
These satisfy equivariance under $\Sigma_n$,
associativity (iterated gluings are order-independent),
and commutativity.

A stable graph records a degeneration of a smooth
algebraic curve into a nodal curve: the
vertices of~$\Gamma$ are the irreducible components, the edges are
the nodes, the genus labels are the genera of the components, and
the half-edges are the marked points.  The set of stable graphs
$\mathsf{Gr}^{\mathrm{st}}_{g,n}$ parametrises the boundary
stratification of the Deligne--Mumford moduli space
$\overline{\cM}_{g,n}$.  Every codimension-one boundary divisor is
a one-edge degeneration; every codimension-two stratum is the
intersection of exactly two codimension-one divisors, appearing
with opposite orientations in the boundary-of-boundary complex.

The \emph{Feynman transform} of~$\cO$, the modular analogue of
the operadic bar construction, replaces trees
in~\eqref{eq:preface-feynman-sum} by stable graphs:
\begin{equation}\label{eq:preface-feynman-sum}
F\cO(g,n)
\;=\;
\bigoplus_{\Gamma\in\mathsf{Gr}^{\mathrm{st}}_{g,n}}
\frac{\hbar^{g(\Gamma)}}{|\operatorname{Aut}(\Gamma)|}
\;\bigotimes_{v\in V(\Gamma)}\cO\bigl(g(v),\mathrm{In}(v)\bigr).
\end{equation}

\subsection*{3.2.\enspace The Feynman transform}

The \emph{differential} of the Feynman transform contracts one edge at a time:
\[
d_{F\cO}(\gamma_\Gamma)
\;=\;
\sum_{e \in E(\Gamma)}
(-1)^{\epsilon(e)}\,
\xi_e(\gamma_{\Gamma/e}),
\]
where $\gamma_{\Gamma/e}$ denotes the image of $\gamma_\Gamma$
under edge contraction along~$e$, applying the operadic
composition~$\xi_e$ to the merging vertex factors;
$\xi_e$ invokes the gluing map
$\xi_{\mathrm{sep}}$ or $\xi_{\mathrm{ns}}$
of~$\cO$ at edge~$e$ and contracts $e$ from~$\Gamma$.
The sign $(-1)^{\epsilon(e)}$ is determined by the
position of~$e$ in the ordering of~$E(\Gamma)$
recorded by the orientation line~$\det(E(\Gamma))$.
The identity $d^2 = 0$ is the codimension-$2$ boundary
cancellation: each pair of edges can be contracted in
either order, and the two terms cancel by the
associativity of~$\cO$.
At genus~$0$ (trees, $\hbar^0=1$), $F\cO$ reduces
to the operadic bar construction~\eqref{eq:preface-feynman-sum}.

When $\cO=\Com$ (the \emph{commutative modular operad}, with
$\Com(g,n)=\Bbbk$ for every stable $(g,n)$), each
vertex factor in~\eqref{eq:preface-feynman-sum} is
one-dimensional, and the Feynman transform becomes the
\emph{stable graph complex}
\begin{equation}\label{eq:preface-fcom}
F\Com(g,n)
\;=\;
\bigoplus_{\Gamma\in\mathsf{Gr}^{\mathrm{st}}_{g,n}}
\frac{\hbar^{g(\Gamma)}}{|\operatorname{Aut}(\Gamma)|}
\;\det\bigl(E(\Gamma)\bigr):
\end{equation}
a chain complex spanned by isomorphism classes of stable graphs,
graded by edge number, with edge-contraction differential.
At genus~$0$, $F\Com(0,n)=B(\Com)(n)$ recovers the tree-level
complex of Ginzburg--Kapranov.

\subsection*{3.3.\enspace The convolution ladder}

To populate the Feynman transform with algebraic data (assigning chiral
amplitudes to vertices and propagators to edges) requires a
convolution mechanism pairing the cooperadic structure of the
skeleton with the operadic structure of the algebra.

At each level of generality, the bar-type construction is the
coefficient of a convolution dg Lie algebra whose Maurer--Cartan
elements classify algebraic structures:
\begin{equation}\label{eq:preface-convolution-ladder}
\begin{array}{r@{\;:\quad}c@{\qquad}l}
\text{algebra} &
  \Hom\bigl(B(\Ass),\,\End_A\bigr)
  & A_\infty\text{-structures on }A \\[4pt]
\text{operad} &
  \Hom_\Sigma\bigl(B(\cP),\,\End_V\bigr)
  & \cP_\infty\text{-structures on }V \\[4pt]
\text{modular} &
  \Hom_\Sigma\bigl(F\cO,\,\End_{\barB(\cA)}\bigr)
  & \text{consistent genus towers}
\end{array}
\end{equation}
The first line is the Hochschild cochain complex; the
second is the deformation complex of Ginzburg--Kapranov;
the third, with $\cO=\Com$, governs this book.  The
\emph{Lie bracket} in each case is the convolution
bracket: for $f, g$ in the convolution hom,
\[
[f, g]
\;:=\;
\mu \circ (f \otimes g) \circ \Delta
\;-\;
(-1)^{|f||g|}\,
\mu \circ (g \otimes f) \circ \Delta,
\]
where $\Delta$ is the cooperadic decomposition
(decomposing a cooperad element along an edge into a
two-vertex composition) and $\mu$ is operadic composition
(composing the output of one operation with an input
of another).

Given a chiral algebra~$\cA$ with bar complex~$\barB(\cA)$,
the \emph{modular convolution dg Lie algebra}
\begin{equation}\label{eq:preface-gmod}
\gAmod
\;:=\;
\Hom_\Sigma\bigl(F\Com,\;\End_{\barB(\cA)}\bigr)
\end{equation}
is the $\cO=\Com$ instance of the modular line
of~\eqref{eq:preface-convolution-ladder}.
The bar complex is an $F\Com$-algebra; the universal MC element
$\Theta_\cA := D_\cA - d_0$ is bar-intrinsic ($D_\cA^2 = 0$
implies $\Theta_\cA \in \operatorname{MC}$), and the five main
theorems of this monograph are projections
of~$\Theta_\cA$ (\S\ref{subsec:chriss-ginzburg-derivation}).

The convolution algebra requires two inputs: a cooperadic coefficient
system (the geometry of configuration spaces) and an operadic
algebra (the chiral algebra on the curve).

The convolution algebra~\eqref{eq:preface-gmod} uses
$\cO=\Com$, the commutative ($E_\infty$) operad: the
stable graphs in~$F\Com$ carry no cyclic ordering at their
vertices.  Replacing $\Com$ by $\Ass$ (the associative
operad) equips each vertex with a cyclic ordering of its
half-edges, and the Feynman transform~$F\!\Ass$ sums over
\emph{ribbon graphs} (fatgraphs) whose genus is the genus of
the thickened embedding surface:
\[
\mathfrak{g}^{\mathrm{mod},\Eone}_\cA
\;:=\;
\Hom_\Sigma\bigl(F\!\Ass,\;
\End_{\barB^{\Eone}(\cA)}\bigr).
\]
This is the algebraic form of the 't~Hooft $1/N$ expansion.
Setting $\hbar = 1/N^2$, the MC element
$\Theta^{\Eone}_\cA \in \operatorname{MC}(\mathfrak{g}^{\mathrm{mod},\Eone}_\cA)$
is the genus expansion
$\sum_g N^{2-2g}F_g(\lambda)$ summed over ribbon graphs weighted
by the genus of their embedding surface.
Planar diagrams ($g=0$) dominate at large~$N$; the shadow
Postnikov tower $\Theta^{E_1,\le r}$ is the truncation to
$r$-point 't~Hooft interactions.
The coinvariant map $F\!\Ass \to F\Com$ projects
$\Theta^{E_1} \mapsto \Theta$:
colour-ordered amplitudes to full amplitudes.
On each \emph{primary line} (a one-dimensional subspace of the
cyclic deformation space $H^2_{\mathrm{cyc}}(\cA,\cA)$ spanned by
a single primary field), the shadow
tower is algebraic of degree~$2$:
the entire infinite sequence is the Taylor expansion of the square
root of a single quadratic form $Q_L$, the \emph{shadow metric}
(\S\ref{sec:shadow-metric}).

\medskip
\noindent\textbf{Remark} (Homotopy types in three stages).
The three levels of the convolution ladder mirror three levels of
homotopy theory.  This parallel
organizes the entire classification programme of Section~6.
\emph{Over a point}: the bar construction
$B(A) = (T^c(s^{-1}\bar A), d_B)$ determines the homotopy type of
an associative algebra; formality ($m_k=0$ for $k \ge 3$)
corresponds to the algebra being intrinsically formal (e.g.\
$\Bbbk[x]/(x^2)$); the Massey products are the obstructions.
\emph{Over a manifold}: the Sullivan minimal model
$(\Lambda V, d)$ determines the rational homotopy type; K\"ahler
manifolds are formal (Deligne--Griffiths--Morgan--Sullivan):
$d = 0$ on the minimal model and the rational homotopy type is
determined by $H^*(X;\mathbb Q)$.  The Heisenberg algebra is the
vertex-algebraic analogue: its shadow obstruction tower terminates at
arity~$2$ (the Gaussian archetype), all higher obstructions
vanish, and the modular homotopy type is determined by~$\kappa$
alone.  \emph{Over a curve at all genera}: the $A_\infty$-products
$m_k$ of the first stage become the modular $L_\infty$-brackets
$\ell_k^{(g)}$; formality becomes the Gaussian archetype
($\ell_k^{(g)}=0$ for $k \ge 3$ at all~$g$); the shadow
Postnikov tower is the modular Massey product tower, classifying
the complexity of the modular homotopy type exactly as the
formality level classifies rational homotopy.
The shadow depth classification of Section~6 makes this analogy
precise: the four classes G, L, C, M correspond to four levels
of modular formality, determined by the vanishing pattern of the
higher brackets~$\ell_k^{(g)}$.
\subsection*{3.4.\enspace Homotopy chiral algebras}

Fix an affine cover $\mathfrak U=\{U_\alpha\}_{\alpha\in I}$ of the
curve~$X$.  The \v{C}ech totalisation
\[
A^{\mathrm{ch}}_\infty
\;:=\;
\check C^\bullet(\mathfrak U;\cA)
\;=\;
\bigoplus_{p\ge 0}
\prod_{\alpha_0<\cdots<\alpha_p}
\cA(U_{\alpha_0}\cap\cdots\cap U_{\alpha_p})
\]
carries a $\mathrm{Ch}_\infty$-algebra structure
(Malikov--Schechtman): the chiral bracket of~$\cA$, restricted to
overlaps of affine opens, does not satisfy the Jacobi identity on
the nose; it satisfies it up to a coherent system of higher
homotopies, the \emph{secondary Borcherds operations}
\[
F_n\colon\mathrm{Lie}(n)\otimes\cY(n)
\;\longrightarrow\;
P_n(\{A^{\mathrm{ch}}_\infty\},\,A^{\mathrm{ch}}_\infty),
\qquad n\ge 2,
\]
encoding derived OPE data at all pole orders.  The operation~$F_2$
is the chiral bracket itself.

The Jacobiator homotopy~$F_3$ arises from the moduli space
$\overline{\mathcal M}_{0,4}\cong\mathbb P^1$: its boundary
$\partial\overline{\mathcal M}_{0,4}$ consists of three points,
corresponding to three OPE compositions
$(a_{(m)}b)_{(n)}c$, $(b_{(m)}c)_{(n)}a$,
$(c_{(m)}a)_{(n)}b$.  The chain
$C_1(\overline{\mathcal M}_{0,4})\cong\Bbbk$ provides a
$1$-chain whose boundary is the alternating sum of the three
vertices; $F_3$ is the chain homotopy witnessing their equality
up to~$d$.

Higher operations $F_n$ are determined inductively by
$C_*(\overline{\mathcal M}_{0,n+1})$ through the homotopy transfer
theorem applied to the inclusion
$H_*(\overline{\mathcal M}_{0,n+1})
\hookrightarrow
C_*(\overline{\mathcal M}_{0,n+1})$.
The cellular chain complex of $\overline{\mathcal M}_{0,n+1}$ is
the chain complex of the associahedron~$K_n$; the transferred
operations $F_n$ are the $A_\infty$-corrections at arity~$n$.

Different affine covers yield quasi-isomorphic
$\mathrm{Ch}_\infty$-algebras: the \v{C}ech-to-derived spectral
sequence degenerates for $\mathcal D$-modules on smooth curves.
The strict chiral algebra~$\cA$ is the $H^0$ of this structure: the
primitive local object is the homotopy chiral algebra; the strict
algebra appears after rectification.  The rectification theorem
(Vallette): the homotopy category of $\mathrm{Ch}_\infty$-algebras
is equivalent to the homotopy category of strict chiral algebras,
via the bar-cobar adjunction at the operadic level.

\subsection*{3.5.\enspace Logarithmic Fulton--MacPherson spaces}

The classical Fulton--MacPherson
compactification records collisions of points on a smooth variety.
Its logarithmic extension, due to Mok, records collisions along
a divisor and provides the normal-crossings boundary structure
on which $D^2=0$ depends.

For a simple-normal-crossing pair $(X,D)$ with $D$ a reduced divisor,
Mok constructs the \emph{logarithmic Fulton--MacPherson
compactification} $\mathrm{FM}_n(X\mathbin{|}D)$: a smooth
variety with corners, compactifying the open configuration space
$\mathrm{Conf}_n(X\setminus D)$, whose boundary stratification is
indexed by \emph{rigid planted-forest types}.

A planted-forest type~$\rho$ consists of:
\begin{itemize}
\item a partition of $\{1,\dots,n\}$ into blocks (the roots of the
forest);
\item for each block, a rooted tree (the planted tree) recording the
hierarchy of collisions;
\item a grid-depth assignment $w_v\in\mathbb Z_{\ge 0}$ to each
vertex, recording the order of tangency with~$D$.
\end{itemize}
The ordinary Fulton--MacPherson compactification is the case
$D=\emptyset$: all grid depths are zero, and the planted trees are
the collision trees of the classical theory.

The \emph{degeneration formula}: for a semistable family $W\to B$
with singular fibre $W_0=\bigcup Y_v$ (components indexed by
vertices of the dual graph), and a rigid type~$\rho$,
\[
\mathrm{FM}_n(W/B)(\rho)
\;\longrightarrow\;
\prod_{v\in V(S_\rho)}
\mathrm{FM}_{I_v}(Y_v\mathbin{|}D_v)
\]
is a proper birational correspondence factoring the global
FM geometry into a fibre product of local FM pieces.

The tropicalisation: planted forests are dual graphs of tropical
curves.  Precisely,
\[
\mathrm{Trop}\bigl(\mathrm{FM}_n(\mathbb C\mathbin{|}D)\bigr)
\;=\;
G_{\mathrm{pf}},
\]
the planted-forest poset with grafting as partial order.  Grafting of
planted forests corresponds to degeneration of the underlying curve;
the poset structure on~$G_{\mathrm{pf}}$ is the face poset of the
boundary stratification, ordered by inclusion of the corresponding
FM boundary strata.  The planted-forest poset
is the combinatorial skeleton of the geometric input, just as the
stable graph complex is the skeleton of the Feynman transform.

The \emph{Mok codimension formula}: for a planted-forest type with
grid depths $(w_1,\dots,w_r)$ and tree vertex counts
$(|V(T_j)|)_{j=1,\dots,s}$,
\[
\mathrm{codim}(W_\rho)
\;=\;
\textstyle\sum_{i=1}^r w_i\;+\;\sum_{j=1}^s(|V(T_j)|-1).
\]
The two summands: grid-depth contributions (tangency with~$D$)
and tree-depth contributions (collision complexity).

For $\mathrm{FM}_3$: seven boundary types.  Codimension~$1$:
$\{12\}$, $\{23\}$, $\{13\}$, $\{123\}$ (four strata, recording
pairwise and triple collisions).  Codimension~$2$:
$\{12{<}123\}$, $\{23{<}123\}$, $\{13{<}123\}$ (three strata,
recording sequential collisions: first a pair, then the third
point joins).

The chain complexes
$\cC^{\log\mathrm{FM}}_{X|D}(n)
:=C_\bullet(\mathrm{FM}_n(X\mathbin{|}D))$ carry cooperadic
structure: the inclusion of boundary strata defines cocomposition
maps.  The \emph{graphwise cocomposition} for a rigid stable
graph~$\Gamma$:
\[
\Delta^{\log}_\Gamma
\;:=\;
(\nu_\Gamma)_*\circ\mathrm{Res}_{D^{\log}_\Gamma}
\;\colon\;
\cC^{\log\mathrm{FM}}_{\mathrm{mod}}(g,n)
\;\longrightarrow\;
\bigotimes_{v\in V(\Gamma)}
\cC^{\log\mathrm{FM}}_{\mathrm{mod}}\bigl(g(v),\,
I_v\sqcup H(v)\bigr)[-|E_{\mathrm{int}}(\Gamma)|],
\]
where $\nu_\Gamma$ is the Mok birational correspondence on the
normalised boundary stratum indexed by~$\Gamma$, and
$\mathrm{Res}_{D^{\log}_\Gamma}$ is the residue along the
logarithmic boundary divisor.  The degree shift
$|E_{\mathrm{int}}(\Gamma)|$ accounts for the codimension of the
stratum (one for each internal edge).

\subsection*{3.6.\enspace The convolution $L_\infty$-algebra}

A twisting morphism $\alpha\colon\cC\to\cP$ between a cooperad and
an operad (satisfying the Maurer--Cartan equation
$\partial\alpha+\alpha\star\alpha=0$ in the convolution algebra)
determines a convolution $sL_\infty$-algebra
$\mathrm{hom}_\alpha(\cC,\cP)$ (Robert-Nicoud--Wierstra, after
Vallette).  The underlying graded vector space:
\[
\mathrm{hom}_\alpha(\cC,\cP)
\;=\;
\prod_{n\ge 1}
\mathrm{Hom}_{\Sigma_n}\bigl(\cC(n),\,\cP(n)\bigr).
\]
The $L_\infty$ brackets:
\[
\ell_k(f_1,\dots,f_k)(x)
\;=\;
\sum
\gamma_{\cP}\!\bigl(
(\alpha\circ 1)(f_1\otimes\cdots\otimes f_k)\,
\Delta^{(k)}_{\cC}(x)
\bigr),
\]
where $\Delta^{(k)}_{\cC}$ is the iterated decomposition of the
cooperad and $\gamma_{\cP}$ is the operadic composition.  The
bracket $\ell_1$ is the convolution differential (pre- and
post-composition with the differentials of~$\cC$ and~$\cP$).  The
bracket $\ell_2$ is the Lie bracket of coderivations.  Higher
brackets $\ell_k$, $k\ge 3$, arise from the higher cooperadic
decompositions and are nontrivial whenever $\cC$ is not
concentrated in a single arity.

The $sL_\infty$-algebra $\mathrm{hom}_\alpha(\cC,\cP)$ extends to
$\infty$-morphisms in \emph{either slot separately}: given a
quasi-isomorphism $\cC\xrightarrow{\sim}\cC'$ of cooperads (or
$\cP\xrightarrow{\sim}\cP'$ of operads), there is an induced
$\infty$-quasi-isomorphism of convolution algebras.  But
\emph{not both simultaneously}: the convolution is functorial in
each slot, but does not assemble into a bifunctor on the
$\infty$-categorical level.  This is a structural constraint:
the MC3 categorical lift of bar-cobar duality must proceed one
slot at a time.

The bar-cobar adjunction $B_\kappa\dashv\Omega_\kappa$ is a
\emph{Quillen equivalence} (Vallette): it induces an equivalence
on homotopy categories.  Different $\mathrm{Ch}_\infty$
presentations yield quasi-isomorphic deformation theories.

\subsection*{3.7.\enspace Assembly}

The \emph{modular convolution $L_\infty$-algebra}:
\begin{equation}\label{eq:pref-convolution}
\mathfrak g^{\mathrm{mod}}_\cA
\;:=\;
\Convinf\!\Bigl(
\cC^{\log\mathrm{FM}}_{\mathrm{mod}},\;
\mathrm{End}_{\mathrm{Ch}_\infty}(A^{\mathrm{ch}}_\infty)
\Bigr).
\end{equation}
The cooperadic input is the log-FM chain cooperad
$\cC^{\log\mathrm{FM}}_{\mathrm{mod}}$: the modular cooperad of
chain complexes on logarithmic FM spaces, with cocomposition given
by the graphwise maps~$\Delta^{\log}_\Gamma$.  The operadic input
is the $\mathrm{Ch}_\infty$-endomorphism operad of the homotopy
chiral algebra~$A^{\mathrm{ch}}_\infty$: the operad of multilinear
maps respecting the transferred homotopy-chiral structure.

One-slot convention: fix the log-FM cooperad (the
``geometric'' slot), vary the chiral algebra input (the
``algebraic'' slot) by $\infty$-morphisms.

The \emph{strict chart}: let $\mathfrak U$ be an affine cover
of~$X$.  The coderivation dg Lie algebra
\[
\mathfrak g^{\mathrm{mod},\log}_\cA(\mathfrak U)
\;:=\;
\Convstr\!\bigl(
\cC^{\log\mathrm{FM}}_{\mathrm{mod}},\;
\mathrm{End}_{\mathrm{Ch}_\infty}(A^{\mathrm{ch}}_\infty)
\bigr)
\]
is the \emph{strict model}: classical Lie bracket (commutator of
coderivations), no higher $L_\infty$ brackets, but the \emph{same}
Maurer--Cartan moduli.  MC elements in the strict chart are in
natural bijection with MC elements in the full convolution
$L_\infty$-algebra.  The strict chart suffices for constructing the
universal MC element and computing shadows; the full $L_\infty$
structure is needed for transfer, formality, and gauge equivalence.

\subsection*{3.8.\enspace The modular bar functor}

In log-FM coordinates, the modular bar functor at type $(g,n)$:
\[
\mathrm B^{\log}_{\mathrm{mod}}(\cA)(g,n)
\;=\;
\bigoplus_{\Gamma\in\mathsf{Gr}^{\mathrm{st}}_{g,n}}
\left(
\bigotimes_{v\in V(\Gamma)}
\bar B^{\mathrm{ch}}(A^{\mathrm{ch}}_\infty;\mathrm{In}(v))
\;\otimes\;
C_\bullet(\mathrm{FM}^{\log}_\Gamma)
\;\otimes\;
\orline{E_{\mathrm{int}}(\Gamma)}
\right)_{\!\mathrm{Aut}(\Gamma)}.
\]
The sum is over stable graphs~$\Gamma$ of type $(g,n)$: graphs with
first Betti number $b_1(\Gamma)+\sum_v g(v)=g$ and $n$ external
legs.  The ingredients:
\begin{itemize}
\item For each vertex~$v\in V(\Gamma)$: the transferred
$\mathrm{Ch}_\infty$-bar contribution
$\bar B^{\mathrm{ch}}(A^{\mathrm{ch}}_\infty;\mathrm{In}(v))$
, the chiral bar complex on the incoming half-edges of~$v$,
computed in the homotopy-chiral framework.
\item For each internal edge: the propagator
$P_\cA=H_\cA^{-1}$, contracting the two half-edges.
\item The geometric factor: the chain complex
$C_\bullet(\mathrm{FM}^{\log}_\Gamma)$ on the log-FM stratum
indexed by~$\Gamma$.
\item The orientation line
$\orline{E_{\mathrm{int}}(\Gamma)}
=\det(\Bbbk\,E(\Gamma))
\otimes\det(H_1(\Gamma;\Bbbk))^{-1}$:
signs from edge orientations and loop orderings.
\item Automorphism quotient: coinvariants under
$\mathrm{Aut}(\Gamma)$.
\end{itemize}

\subsection*{3.9.\enspace The six-component differential}

The total differential has six components, whose mutual
cancellations constitute $D^2=0$:
\[
D^{\log}_{\mathrm{mod}}
\;=\;
\underbrace{d_{\check C}}_{\text{\v Cech}}
\;+\;
\underbrace{d_{\mathrm{Ch}_\infty}}_{\text{transferred chiral}}
\;+\;
\underbrace{d_{\mathrm{coll}}}_{\text{collision}}
\;+\;
\underbrace{d_{\mathrm{sew}}}_{\text{separating}}
\;+\;
\underbrace{d_{\mathrm{pf}}}_{\text{planted-forest}}
\;+\;
\underbrace{\hbar\,\Delta}_{\text{genus-raising}}.
\]
The six components, their geometric sources, and their action on a
pure tensor $a\otimes\eta$ indexed by a stable graph~$\Gamma$:

$d_{\check C}$: the \v{C}ech differential of the cover
$\mathfrak U$.  Acts on the \v{C}ech indices of the vertex labels.
Source: the nerve of the cover.

$d_{\mathrm{Ch}_\infty}$: the transferred chiral differential
on each vertex contribution.  Acts on the
$\mathrm{Ch}_\infty$-bar complex at each vertex.  Source: the
secondary Borcherds operations~$F_n$.

$d_{\mathrm{coll}}$: the collision (residue) differential.
Contracts an internal edge of~$\Gamma$ by extracting the OPE
residue at the corresponding codimension-one collision stratum.
Source: codimension-one faces of $\overline{\mathrm{FM}}_n(X)$.

$d_{\mathrm{sew}}$, $d_{\mathrm{pf}}$, and $\hbar\,\Delta$: the three
positive-genus boundary operators.  On a pure tensor $a\otimes\eta$
indexed by~$\Gamma$:
\begin{align*}
d_{\mathrm{sew}}(a\otimes\eta)
&\;=\;
\sum_{e\in E_{\mathrm{sep}}(\Gamma)}
\pm\,\mu_e(a)\otimes(\xi_e)_*\,
\mathrm{Res}_{D_e^{\log}}(\eta),
\\[4pt]
d_{\mathrm{pf}}(a\otimes\eta)
&\;=\;
\sum_{F\in\mathsf{PF}^{\mathrm{rig}}(\Gamma)}
\pm\,\mu_F(a)\otimes(\xi_F)_*\,
\mathrm{Res}_{D_F^{\log}}(\eta),
\\[4pt]
\hbar\,\Delta(a\otimes\eta)
&\;=\;
\hbar\sum_{e\in E_{\mathrm{ns}}(\Gamma)}
\pm\,\mathrm{Tr}_e(a)\otimes(\xi_e)_*\,
\mathrm{Res}_{D_e^{\log}}(\eta).
\end{align*}
Separating edges $E_{\mathrm{sep}}(\Gamma)$ (cutting the graph
into two connected components)
$\to d_{\mathrm{sew}}$: the clutching morphism, gluing two
lower-genus curves along a node.
Non-separating edges $E_{\mathrm{ns}}(\Gamma)$ (whose creation
increases $b_1$ by one) $\to\hbar\Delta$: the genus-raising operator,
self-gluing a curve at two marked points.  Planted-forest strata
$\mathsf{PF}^{\mathrm{rig}}(\Gamma)$ $\to d_{\mathrm{pf}}$:
the log-FM degeneration corrections.

The maps: $\mu_e$ contracts the algebra labels at the two half-edges
of~$e$ using the chiral bracket; $\mathrm{Tr}_e$ contracts using the
bilinear pairing (supertrace over the two half-edges of~$e$);
$\mu_F$ applies the tree-level multilinear operation dictated by the
planted forest~$F$.  The maps $(\xi_e)_*$ and $(\xi_F)_*$ are the
pushforward along the normalisation of the boundary stratum.

The planted-forest differential as push--pull:
\[
d_{\mathrm{pf}}
\;=\;
\sum_{\rho\in\mathsf{PF}^{\mathrm{rig}}}
\epsilon_\rho\,
(\kappa_\rho)_*\,\mathrm{pr}_\rho^*\otimes\mu_\rho\,,
\]
where $\mathrm{pr}_\rho^*$ pulls back chains to the planted-forest
stratum and $(\kappa_\rho)_*$ pushes forward along the Mok
birational correspondence.  This is Mok's degeneration formula,
internalised in the convolution algebra: the push--pull
correspondence on log-FM strata becomes a summand of the total
differential.

\subsection*{3.10.\enspace $D^2=0$}

The nilpotence $(D^{\log}_{\mathrm{mod}})^2=0$ holds by three
cancellation mechanisms, each consuming a distinct geometric fact:
\begin{enumerate}[label=(\roman*)]
\item \emph{Vertex labels}: $d_{\check C}^{\,2}=0$,
$d_{\mathrm{Ch}_\infty}^{\,2}=0$, and their anticommutator
$\{d_{\check C},d_{\mathrm{Ch}_\infty}\}=0$ by the
$\mathrm{Ch}_\infty$-algebra axioms on
$A^{\mathrm{ch}}_\infty$.
\item \emph{One-edge expansions}: the anticommutator of a
vertex differential ($d_{\check C}$ or
$d_{\mathrm{Ch}_\infty}$) with an edge-contraction differential
($d_{\mathrm{coll}}$, $d_{\mathrm{sew}}$, $d_{\mathrm{pf}}$,
or $\hbar\Delta$) vanishes by the Leibniz rule for coderivations.
Each edge contraction is a coderivation of the coalgebra
structure, and the vertex differentials are derivations of the
algebra structure.
\item \emph{Codimension-two cancellation}: the sum of all
products of two distinct edge-contraction operators vanishes.
The codimension-two boundary of
Mok's log-FM compactification is a normal-crossings divisor
(Mok, Theorem~3.3.1), and each codimension-two face appears as
the intersection of exactly two codimension-one faces.  The
two boundary contributions cancel because the face maps compose
with opposite orientations.  This is $\partial^2=0$ for the
boundary of a manifold with corners, lifted through the
residue correspondence.
\end{enumerate}

The third mechanism is the nontrivial one.  The normal-crossings
property of Mok's compactification is essential: it guarantees
that every codimension-two intersection is transverse and
contributes to exactly one cancelling pair.  Without normal crossings,
the codimension-two faces could have excess intersection, and the
cancellation would fail.
% ====================================================================
\section*{4.\quad The universal Maurer--Cartan element}
% ====================================================================

\subsection*{4.1.\enspace $\Gamma$-amplitudes and Taylor coefficients}

Each stable graph produces a multilinear operation on the convolution
algebra.  The operation is built from three ingredients: chiral
operations at vertices, propagators along edges, and geometric
factors from the log-FM strata.  The Taylor coefficients of the
modular $L_\infty$-structure are obtained by summing these
$\Gamma$-amplitudes over all stable graphs of fixed genus and
vertex count.

For a stable graph $\Gamma\in\mathsf{Gr}^{\mathrm{st}}$ with
$|V(\Gamma)|=k$ vertices and elements $f_1,\dots,f_k\in\gAmod$
assigned to those vertices, the \emph{$\Gamma$-amplitude} assembles
the chiral operations, the propagator, and the modular twisting
morphism into a single multilinear operation.  Let
$\mu_\Gamma\colon\bigotimes_{v\in V(\Gamma)}A^{\otimes n(v)}\to A$
denote the graph composition: at each vertex~$v$ of genus~$g(v)$ and
valence~$n(v)$, place the transferred chiral operation
$m^{(h)}_{g(v),n(v)}$; along each internal edge, contract with the
propagator~$P_\cA=\iota\circ\pi$ (homotopy retraction of the
augmentation ideal to its cohomology).  Write
$\alpha^{\mathrm{mod}}_\Gamma$ for the component of the modular
twisting morphism on~$\Gamma$, and
$\Delta^{\log}_\Gamma\colon\cC^{\log\mathrm{FM}}_{\mathrm{mod}}
\to\bigotimes_{v\in V(\Gamma)}\cC^{\log\mathrm{FM}}_{g(v),n(v)}$
for the cooperadic cocomposition.  The $\Gamma$-amplitude is:
\[
\ell_\Gamma(f_1,\dots,f_k)
\;=\;
\mu_\Gamma\circ
(\alpha^{\mathrm{mod}}_\Gamma\otimes f_1\otimes\cdots\otimes f_k)
\circ\Delta^{\log}_\Gamma.
\]
This is a $k$-linear map
$\ell_\Gamma\colon(\gAmod)^{\otimes k}\to\gAmod$ of cohomological
degree $2-2g(\Gamma)-k$, where $g(\Gamma)=b_1(\Gamma)+\sum_v g(v)$
is the total genus.

The modular $L_\infty$ structure on~$\gAmod$ has Taylor coefficients
obtained by summing over all stable graphs of fixed genus and vertex
count:
\[
\ell_k^{(g)}
\;=\;
\sum_{\substack{
\Gamma\in\mathsf{Gr}^{\mathrm{st}},\;|V(\Gamma)|=k\\
b_1(\Gamma)+\sum_v g(v)=g}}
\frac{1}{|\operatorname{Aut}(\Gamma)|}\;\ell_\Gamma.
\]
Here $\ell_k^{(g)}$ is a symmetric $k$-linear bracket of genus~$g$.
The full modular $L_\infty$ structure is the formal sum
$\ell=\sum_{g\ge 0}\sum_{k\ge 1}\hbar^g\,\ell_k^{(g)}/k!$, and the
homotopy Jacobi identity is encoded by $D^2=0$ on the total
convolution algebra.

\medskip

\noindent\textbf{Explicit low-order Taylor coefficients.}\enspace
The first several brackets admit direct geometric description.  At
tree level ($g=0$), the binary bracket is the Lie bracket on
cohomology transferred through the homotopy retraction data
$(\pi,\iota,h)$:
\[
\ell_2^{(0)}(\alpha,\beta)
\;=\;
\pi\bigl[m_2\bigl(\iota(\alpha),\iota(\beta)\bigr)\bigr].
\]
The ternary bracket is a sum over binary trees with three leaves:
\begin{align*}
\ell_3^{(0)}(\alpha,\beta,\gamma)
&=\sum_{T\in\mathsf{Trees}_3}
|\operatorname{Aut}(T)|^{-1}\,
(\pi\circ m_T^{(h)}\circ\iota^{\otimes 3})(\alpha,\beta,\gamma)\\[3pt]
&=\pi\Bigl(
m_2\bigl(h\,m_2(\iota\alpha,\iota\beta),\,\iota\gamma\bigr)
+m_2\bigl(\iota\alpha,\,h\,m_2(\iota\beta,\iota\gamma)\bigr)\\
&\qquad\quad
+m_2\bigl(h\,m_2(\iota\alpha,\iota\gamma),\,\iota\beta\bigr)
\Bigr).
\end{align*}
There are three binary trees in $\mathsf{Trees}_3$ (one for each
channel $s$, $t$, $u$), each with trivial automorphism group.  The
homotopy~$h$ propagates the intermediate state through~$P_\cA$
before re-composing.  This is the classical homological perturbation
lemma in its $L_\infty$ incarnation.

The quaternary bracket sums over the fifteen labeled trees in
$\mathsf{Trees}_4$ (two unlabeled topologies: three balanced
$((ab)(cd))$ and twelve caterpillar $(((ab)c)d)$):
\begin{align*}
\ell_4^{(0)}(\alpha,\beta,\gamma,\delta)
&=\sum_{T\in\mathsf{Trees}_4}
\pm\,|\operatorname{Aut}(T)|^{-1}\,
(\pi\circ m_T^{(h)}\circ\iota^{\otimes 4})
(\alpha,\beta,\gamma,\delta).
\end{align*}
Each tree~$T$ has two internal edges, hence two propagator
insertions.  The signs are Koszul signs from the symmetric monoidal
structure.  The two topologies reflect the two vertices of the
graph complex $\mathsf{Gr}_4^{\mathrm{tree}}$.

The first genus-raised bracket is unary:
\[
\ell_1^{(1)}(\alpha)
\;=\;
\operatorname{tr}(P_\cA\circ\alpha\circ
\delta^{\mathrm{ns}})
\;=\;
\sum_{i}
\langle e^i,\,\alpha(e_i)\rangle_{\mathrm{Sh}},
\]
where $\{e_i\}$, $\{e^i\}$ is a dual basis for the cyclic pairing
on~$H^*(\bar\cA)$ and $\delta^{\mathrm{ns}}$ is the non-separating
node operator.  Geometrically, this is the BV operator: the unique
genus-one graph with one vertex and one self-loop.  The trace is
over the propagator contracting the two half-edges at the
non-separating node of~$\overline{\cM}_{1,1}$.

The genus-one binary bracket accounts for the separating node
of~$\overline{\cM}_{1,2}$:
\[
\ell_2^{(1)}(\alpha,\beta)
\;=\;
\operatorname{tr}\bigl(
P_\cA\circ m_2(\iota\alpha,-)
\circ\delta^{\mathrm{ns}}\circ\iota\beta
\bigr)
\;+\;
(\alpha\leftrightarrow\beta).
\]
These low-order brackets are the only data needed for all shadow
computations through arity~$4$.

\subsection*{4.2.\enspace The bar-intrinsic construction}

The construction requires no equation to solve.
The element $\Theta_\cA$ is extracted
from a differential that already squares to zero.

The total bar differential
$D_\cA\colon\mathrm{B}^{\mathrm{mod}}(\cA)\to
\mathrm{B}^{\mathrm{mod}}(\cA)$ acts on the modular bar complex.
Decompose $D_\cA=d_0+\Theta_\cA$, where
$d_0=d_{\mathrm{int}}+[\tau,-]$ is the tree-level local part: the
internal differential of~$\cA$ plus the commutator with the tautological
twisting morphism~$\tau$.  The \emph{universal Maurer--Cartan element}
is the remainder:
\begin{equation}\label{eq:pref-theta}
\Theta_\cA
\;:=\;
D_\cA-d_0
\;=\;
\sum_{\Gamma\in\mathsf{Gr}^{\mathrm{st}}}
\frac{W^{\log\mathrm{FM}}_\Gamma}{|\operatorname{Aut}(\Gamma)|}
\otimes\Phi^\cA_\Gamma
\;\in\;
\operatorname{MC}(\gAmod).
\end{equation}
Here $W^{\log\mathrm{FM}}_\Gamma\in
H^*(\overline{\cM}^{\log}_{g(\Gamma),n(\Gamma)})$ is the log-FM
weight (the fundamental class of the boundary stratum indexed
by~$\Gamma$), and
$\Phi^\cA_\Gamma\in\operatorname{Hom}(\bar\cA^{\otimes
n(\Gamma)},\Bbbk)$ is the chiral amplitude on~$\Gamma$ (propagators
on internal edges, operations at vertices, cyclic trace at the output).

The MC property is immediate: $D_\cA^{\,2}=0$ by the geometric fact
that $\overline{\cM}_{g,n}^{\log}$ has normal-crossings boundary;
$d_0^2=0$ by construction; expanding $(d_0+\Theta_\cA)^2=0$ gives
\[
d_0\Theta_\cA+\Theta_\cA\,d_0
+\Theta_\cA^2=0
\qquad\Longleftrightarrow\qquad
[d_0,\Theta_\cA]+\tfrac12[\Theta_\cA,\Theta_\cA]=0.
\]
The MC property is not proved by solving a system of equations;
it is a formal consequence of $\partial^2=0$ on the moduli space
of curves.  The construction requires no simple-Lie restriction,
no convergence hypothesis, and no choice of basis.

\subsection*{4.3.\enspace $\Theta_\cA$ as universal modular twisting morphism}

The Maurer--Cartan space of the modular convolution $L_\infty$
algebra is identified with the space of modular twisting morphisms:
\[
\operatorname{MC}_\bullet\!\bigl(\gAmod\bigr)
\;\simeq\;
\operatorname{Tw}_{\alpha^{\mathrm{mod}}}\!\Bigl(
\cC^{\log\mathrm{FM}}_{\mathrm{mod}},\,
\operatorname{End}_{\mathrm{Ch}_\infty}(A^{\mathrm{ch}}_\infty)
\Bigr).
\]
Under this identification, $\Theta_\cA$ is the \emph{universal
modular twisting morphism}, the operadic analogue of the canonical
flat connection on a principal bundle.  A twisting
morphism $\alpha\colon\cC\to\cP$ between a cooperad and an operad
determines a twisted composition product $\cC\circ_\alpha\cP$ whose
differential squares to zero if and only if~$\alpha$ satisfies the
MC equation.  $\Theta_\cA$ is the unique twisting morphism that
simultaneously twists the modular bar complex and intertwines with
the log-FM boundary structure.

The principal-bundle analogy is exact.  The modular bar
bundle $\mathrm{B}^{\log}_{\mathrm{mod}}(\cA)\to
\overline{\cM}_{g,n}$ is the principal bundle; $\Theta_\cA$ is the
connection; the MC equation is the flatness condition; the shadow
tower (Section~6) is the Chern--Weil theory.  The structure group is
the pro-unipotent MC gauge group
$\exp(\mathfrak g^{\mathrm{mod},0}_\cA)$.

\subsection*{4.4.\enspace Tridegree, depth, and convergence}

Each coefficient of~$\Theta_\cA$ carries a natural tridegree
\[
(g,n,d)
\;=\;
(\text{loop genus},\;\text{external arity},\;\text{log boundary depth}),
\]
where $d(\rho)=\#E_{\mathrm{sep}}(\Gamma_\rho)+
\#E_{\mathrm{ns}}(\Gamma_\rho)+\operatorname{depth}_{\mathrm{pf}}
(\Gamma_\rho)$ is the codimension of the log-FM stratum indexed by
the degeneration pattern~$\rho$.  Here $E_{\mathrm{sep}}$ counts
separating edges, $E_{\mathrm{ns}}$ counts non-separating edges, and
$\operatorname{depth}_{\mathrm{pf}}$ counts planted-forest depth
levels.  The total depth equals the codimension of the stratum
$D^{\log}_\rho$ in the log-FM compactification.

The depth filtration
$F^d\gAmod=\bigoplus_{d'\ge d}(\gAmod)_{*,*,d'}$ makes
the convolution algebra complete:
\[
\gAmod\;=\;\varprojlim_{d}\;\gAmod/F^d\gAmod.
\]
The inverse limit
$\Theta_\cA=\varprojlim_r\Theta_\cA^{\le r}$ converges
unconditionally: no analytic input, no growth estimate, no
restriction on the algebra~$\cA$.  The convergence is purely
algebraic, guaranteed by the completeness of the depth filtration.

The tridegree decomposition organizes computation.  At fixed
$(g,n)$, only finitely many stable graph types~$\Gamma$ contribute
(by stability: $2g(\Gamma)-2+n(\Gamma)>0$ forces a finite graph
set).  The depth filtration refines this further: at depth~$d$,
the stratum has codimension~$d$ in $\overline{\cM}_{g,n}^{\log}$,
and the amplitude $\Phi^\cA_\Gamma$ has internal-edge count
(hence propagator insertions) bounded by~$d$.

\subsection*{4.5.\enspace The weight filtration}

The weight filtration is the primary organizational tool for the MC
equation.  Decompose by internal-edge count (equivalently, by total
propagator insertions):
\[
\Theta_\cA\;=\;\sum_{r\ge 1}\Theta^{[r]}_\cA,
\qquad
\Theta^{[r]}_\cA\;=\;
\sum_{\substack{\Gamma\in\mathsf{Gr}^{\mathrm{st}}\\
|E_{\mathrm{int}}(\Gamma)|=r}}
\frac{W^{\log\mathrm{FM}}_\Gamma}{|\operatorname{Aut}(\Gamma)|}
\otimes\Phi^\cA_\Gamma.
\]
The MC equation decomposes by weight into an inductive tower:
\begin{alignat*}{2}
&\text{Weight }1{:}\quad
&&[D_{\mathrm{loc}},\Theta^{[1]}_\cA]=0,\\[4pt]
&\text{Weight }2{:}\quad
&&[D_{\mathrm{loc}},\Theta^{[2]}_\cA]
+\tfrac12[\Theta^{[1]}_\cA,\Theta^{[1]}_\cA]=0,\\[4pt]
&\text{Weight }3{:}\quad
&&[D_{\mathrm{loc}},\Theta^{[3]}_\cA]
+[\Theta^{[1]}_\cA,\Theta^{[2]}_\cA]=0,\\[4pt]
&\text{Weight }N{:}\quad
&&[D_{\mathrm{loc}},\Theta^{[N]}_\cA]
+\tfrac12\sum_{\substack{i+j=N\\i,j\ge 1}}
[\Theta^{[i]}_\cA,\Theta^{[j]}_\cA]=0.
\end{alignat*}
At each stage, $[D_{\mathrm{loc}},\Theta^{[N]}]$ is determined by
the quadratic error from previous stages.  The obstruction to
extending from weight~$N-1$ to weight~$N$ lies in
$H^2(\gAmod/F^{N+1},D_{\mathrm{loc}})$.  The bar-intrinsic
construction solves all stages simultaneously.

\medskip

\noindent\textbf{Weight~$1$: boundary divisors.}\enspace
The weight-one component $\Theta^{[1]}_\cA$ lives on boundary
divisors of moduli spaces.  In degree $(0,4)$: the three boundary
points of $\overline{\cM}_{0,4}\cong\mathbb P^1$, corresponding to
the three channels $(12|34)$, $(13|24)$, $(14|23)$:
\[
\Theta^{[1]}_\cA\big|_{(0,4)}
=[\delta_s]\otimes\Phi_s
+[\delta_t]\otimes\Phi_t
+[\delta_u]\otimes\Phi_u.
\]
Here $[\delta_s]$, $[\delta_t]$, $[\delta_u]$ are the fundamental
classes of the three boundary points $\{0,1,\infty\}\subset\mathbb
P^1$, and $\Phi_s$, $\Phi_t$, $\Phi_u$ are the corresponding chiral
four-point amplitudes (binary composition in channel $s$, $t$, $u$
respectively).  The weight-one MC equation
$[D_{\mathrm{loc}},\Theta^{[1]}]=0$ at $(0,4)$ reads:
\[
\Phi_s+\Phi_t+\Phi_u=F_3,
\]
where $F_3$ is the Malikov--Schechtman Jacobiator homotopy, the
failure of the chiral bracket to satisfy the Jacobi identity on the
nose.  This is the first Borcherds identity: the Jacobiator is a
boundary in the bar complex.

In degree $(1,1)$: the single boundary divisor
$\delta_{\mathrm{irr}}\subset\overline{\cM}_{1,1}$ (the irreducible
nodal cubic):
\[
\Theta^{[1]}_\cA\big|_{(1,1)}
=[\delta_{\mathrm{irr}}]\otimes\Delta,
\]
where $\Delta=\sum_i e_i\otimes e^i$ is the Casimir element of the
cyclic pairing, the non-separating sewing propagator.  The weight-one
MC equation at $(1,1)$ encodes the consistency of the one-loop trace
with the modular structure.

In degree $(0,5)$: the weight-one component restricts to the ten
boundary divisors of $\overline{\cM}_{0,5}$ (the Petersen graph), and
the MC equation recovers the pentagon identity for the $L_\infty$
structure.  The entire $A_\infty$ hierarchy is the tree-level,
genus-zero projection of a single MC element.

\medskip

\noindent\textbf{Weight~$2$: the first planted-forest layer.}\enspace
At weight~$2$, the codimension-two strata of the log-FM
compactification enter.  These strata have two types: classical
(products of two boundary divisors in $\overline{\cM}_{g,n}$) and
genuinely logarithmic (planted-forest strata of
$\operatorname{FM}_n(X\mathbin{|}D)$ with no counterpart in the
classical Deligne--Mumford compactification).  Mok's rigid
planted-forest types enter at this weight.

The weight-two MC equation is:
\[
[D_{\mathrm{loc}},\Theta^{[2]}_\cA]
\;=\;
-\tfrac12[\Theta^{[1]}_\cA,\Theta^{[1]}_\cA].
\]
The right-hand side is a quadratic expression in the weight-one data:
the square of the boundary-divisor class.  The planted-forest
correction $\Theta^{[2]}_{\mathrm{pf}}$ is the new
contribution: it records how collision limits in the planted-forest
sector of $\operatorname{FM}_n(X\mathbin{|}D)$ correct the naive
square.

For the $\mathcal W_3$ central-parameter line, the self-coupling of
the unique genus-one tangent direction at weight one is $d_0$-exact
(the quadratic self-interaction is removable by gauge), so any
nontrivial genus-two obstruction comes from this planted-forest sector.
Cubic gauge triviality (Section~6.3): the weight-$2$ obstruction
vanishes by gauge; the first genuine invariant is at weight~$3$.

\subsection*{4.6.\enspace The all-genus recursion}

Project the MC equation to fixed genus~$g$ and arity~$n$:
\[
d\Theta^{(g,n)}_\cA
+\tfrac12
\!\!\!
\sum_{\substack{g_1+g_2=g\\n_1+n_2=n+2}}
\!\!\!
\ell_2^{(0)}(\Theta^{(g_1,n_1)}_\cA,\Theta^{(g_2,n_2)}_\cA)
+\Delta_{\mathrm{ns}}\,\Theta^{(g-1,n+2)}_\cA
+\sum_{k\ge 3}\frac{1}{k!}
\ell_k^{(\mathrm{tree})}(\Theta_\cA,\dots,\Theta_\cA)^{(g,n)}
=0.
\]
The four terms have direct geometric meaning.  \emph{Internal
differential}: the action of~$d$ on the bar labels at fixed
$(g,n)$.  \emph{Separating clutching}: the sum over splittings
$g_1+g_2=g$, $n_1+n_2=n+2$, identifying the separating node as a
binary bracket $\ell_2^{(0)}$ applied to lower-genus and
lower-arity MC data.  \emph{Non-separating BV operator}: the
contraction $\Delta_{\mathrm{ns}}$ lowers arity by~$2$ and raises
genus by~$1$, applied to $\Theta^{(g-1,n+2)}$.
\emph{Planted-forest corrections}: the higher brackets
$\ell_k^{(\mathrm{tree})}$ for $k\ge 3$ encode the genuinely
logarithmic corrections from Mok's planted-forest strata.

This recursion determines $\Theta^{(g,n)}_\cA$ inductively from
lower $(g',n')$ in lexicographic order: $g'<g$, or $g'=g$ and
$n'<n$.  The base cases are
$\Theta^{(0,3)}_\cA$ (the chiral bracket) and
$\Theta^{(0,4)}_\cA$ (the Jacobiator data from weight~$1$).
The recursion terminates at each $(g,n)$: only finitely many stable
graphs contribute.

\medskip

\noindent\textbf{The clutching identity.}\enspace
On each rigid boundary stratum~$\rho$ of the log-FM
compactification, the restriction of~$\Theta_\cA$ factors as a
tensor product over vertices of the dual graph:
\[
\Theta_\cA\big|_\rho
\;=\;
(\kappa_\rho)_*\!\left(
\bigotimes_{v\in V(S_\rho)}\Theta_{\cA,v}
\right).
\]
Here $S_\rho$ is the stable dual graph of the stratum~$\rho$,
$\Theta_{\cA,v}$ is the MC element restricted to the irreducible
component at vertex~$v$, and $\kappa_\rho$ is the clutching
morphism: the amplitude on the degenerate curve equals the product
of amplitudes on the irreducible components, sewn by propagators
along the nodes.  It is
the MC-level incarnation of the sewing axiom for conformal field
theory, and the starting point for the clutching law of the quartic
shadow (Section~6.3).

\bigskip
\noindent
Every invariant in this preface is a projection of~$\Theta_\cA$:
the curvature~$\kappa$, the spectral discriminant~$\Delta_\cA$,
the shadow metric~$Q_L$, the sewing amplitudes, the $\hat A$-genus,
the Fredholm determinant, and the quartic contact
invariant~$Q^{\mathrm{contact}}$.
The five main theorems are five projections of~$\Theta_\cA$.
The principal projections:

\medskip
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lll}
\textbf{Projection of $\Theta_\cA$}
  & \textbf{Invariant} & \textbf{Section} \\
\hline
Scalar ($r=2$, genus tower)
  & $\kappa(\cA)$, $F_g$, $\hat A$-genus
  & \S2 \\[2pt]
Binary genus-$0$ residue
  & classical $r$-matrix, Yangian seed
  & \S7.7 \\[2pt]
Binary Verdier dual
  & complementarity $Q_g \oplus Q_g^!$
  & \S2 \\[2pt]
Bar-cobar counit
  & inversion $\Omega(\barB(\cA))\xrightarrow{\sim}\cA$
  & \S1 \\[2pt]
Chiral Hochschild
  & $\mathrm{ChirHoch}^*(\cA)$, deformation ring
  & \S9 \\[2pt]
Spectral discriminant
  & $\Delta_\cA(x)$, genus-$1$ Hessian
  & \S5 \\[2pt]
Cubic shadow ($r=3$)
  & gauge-trivial obstruction
  & \S6 \\[2pt]
Quartic resonance ($r=4$)
  & $\mathfrak Q^{\mathrm{contact}}$, clutching law
  & \S6 \\[2pt]
MC tautological descent
  & shadow CohFT, $R^*(\overline{\cM}_{g,n})$
  & \S5 \\[2pt]
Primitive kernel
  & shell equations, branch BV
  & \S5 \\[2pt]
Dirichlet--sewing lift
  & $S_\cA(u)$, Euler--Koszul class
  & \S8 \\[2pt]
Swiss-cheese colour decomposition
  & $\alpha_T$, six projections (Vol.~II)
  & \S10
\end{tabular}
\end{center}
\medskip

\noindent
These five theorems are five projections of a single object:
the universal Maurer--Cartan element
$\Theta_\cA := D_\cA - d_\cA^{(0)}$
in the modular convolution algebra~$\gAmod$.
The existence of~$\Theta_\cA$ is encoded by the bar-cobar adjunction:
Theorem~A constructs the arena in which~$\Theta_\cA$ lives.
Bar-cobar inversion proves that~$\Theta_\cA$ is a complete invariant:
Theorem~B recovers~$\cA$ from~$\Theta_\cA$.
Verdier duality decomposes~$\Theta_\cA$ into complementary halves:
Theorem~C splits the genus tower into Lagrangian summands.
The leading coefficient of~$\Theta_\cA$ is the modular characteristic:
Theorem~D extracts the scalar $\kappa(\cA)$ with $\hat A$-genus generating function.
The coefficient ring of~$\Theta_\cA$ is the chiral Hochschild complex:
Theorem~H identifies the deformation ring.

The finite-order projections of~$\Theta_\cA$ form a Postnikov tower
$\Theta_\cA^{\leq 2} \to
\Theta_\cA^{\leq 3} \to
\Theta_\cA^{\leq 4} \to \cdots$
whose generating function is algebraic of degree~$2$: on each
primary line~$L$, the weighted shadow generating function
$H(t) = t^2\sqrt{Q_L(t)}$ for a quadratic polynomial~$Q_L$
determined by three seed invariants $(\kappa, \alpha, S_4)$.
The inverse limit
$\Theta_\cA = \varprojlim_r \Theta_\cA^{\leq r}$
is proved to exist and to be automatically Maurer--Cartan
because $D_\cA^2 = 0$.

In three dimensions, $\Theta_\cA$ extends to an open/closed
Maurer--Cartan element
$\Theta^{\mathrm{oc}}_\cA = \Theta_\cA + \sum_j \mu^{M_j}$
that packages the complete holomorphic-topological quantum field
theory on $\mathbb C_z \times \mathbb R_t$: the bar complex encodes
the closed (holomorphic) colour, the coproduct encodes the open
(topological) colour, and the chiral derived center
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)$ is the universal bulk
(Volume~II).

\medskip
\noindent
\textbf{Corollary} (MC replaces the sum over topologies).
On the Koszul locus, the tree-level complex carries a contracting
homotopy (from the PBW degeneration), so the genus-$g$ component
$\Theta^{(g)}$ is determined (up to the contractible ambiguity
in the choice of strong deformation retract) by induction from
$\Theta^{(0)}$.  No free parameters appear at any genus; the
contracting homotopy is unique up to homotopy, and distinct
choices yield gauge-equivalent MC elements.  No choice of bulk
topologies is required.  The genus expansion is computed algebraically
from the genus-$0$ chiral bracket by the clutching recursion of
Section~4.6, not approximated perturbatively.  The
Maloney--Witten problem (negative Fourier coefficients in the
Poincar\'e series) does not arise: the MC equation determines each $F_g$ uniquely
by algebraic induction, without summing over bulk topologies at fixed genus.
The non-perturbative sum over distinct three-manifold topologies is
outside the scope of the MC framework.

% ====================================================================
\section*{5.\quad The modular tangent complex and Chern--Weil theory}
% ====================================================================

The MC element $\Theta_\cA$ exists
unconditionally and satisfies
$D\Theta_\cA + \tfrac{1}{2}[\Theta_\cA,\Theta_\cA] = 0$.  Its
deformation theory is controlled by the modular tangent complex,
obtained by twisting the convolution algebra by $\Theta_\cA$ itself.

\subsection*{5.1.\enspace The $L_\infty$-twisted differential}

The MC element $\Theta_\cA$ twists the convolution differential.  For $x\in\gAmod$:
\[
d_{\Theta_\cA}(x)
\;:=\;
\sum_{n\ge 0}\sum_{g\ge 0}
\frac{\hbar^g}{n!}\,
\ell_{n+1}^{(g)}(\Theta_\cA^{\otimes n},x).
\]
Expanding:
\[
d_{\Theta_\cA}(x)
\;=\;
d(x)
\;+\;
[\Theta_\cA,x]
\;+\;
\tfrac{1}{2!}\ell_3^{(0)}(\Theta_\cA,\Theta_\cA,x)
\;+\;
\hbar\,\ell_1^{(1)}(x)
\;+\;
\hbar\,\ell_2^{(1)}(\Theta_\cA,x)
\;+\;\cdots
\]
In the strict chart (the dg Lie model $\Convstr$), this collapses to:
\[
d_{\Theta_\cA}(x)\;=\;d(x)+[\Theta_\cA,x].
\]
The identity $d_{\Theta_\cA}^2=0$ is equivalent to the MC equation
for~$\Theta_\cA$.

\subsection*{5.2.\enspace The modular tangent complex}

The \emph{modular tangent complex at~$\Theta_\cA$} is the twisted
cochain complex:
\[
T^{\mathrm{mod}}_{\Theta_\cA}
\;:=\;
(\gAmod,\;d_{\Theta_\cA}).
\]
Its cohomology governs deformations of~$\Theta_\cA$:
\begin{align*}
H^0(T^{\mathrm{mod}}_{\Theta_\cA})
&=\text{infinitesimal automorphisms of~$\Theta_\cA$}
  &&\text{(stabiliser)},\\[3pt]
H^1(T^{\mathrm{mod}}_{\Theta_\cA})
&=\text{first-order deformations of~$\Theta_\cA$}
  &&\text{(tangent space)},\\[3pt]
H^2(T^{\mathrm{mod}}_{\Theta_\cA})
&=\text{obstructions to extending deformations}
  &&\text{(obstruction space)}.
\end{align*}
When $H^2=0$, the MC moduli is smooth at~$\Theta_\cA$.
When $H^1=0$, the MC element is rigid: every nearby element is
gauge-equivalent.

For a one-parameter family $\cA_t$ varying continuously in
level~$k(t)$ or central charge~$c(t)$, the tangent complex
$T^{\mathrm{mod}}_{\Theta_{\cA_t}}$ forms a local system over the
parameter space, and the obstruction class traces a path
in~$H^2$.  The vanishing locus of this obstruction path is the
moduli of liftable deformations.

\subsection*{5.3.\enspace Three characteristic projections}

Three successive
projections of $\Theta_\cA$ capture progressively finer structure:
$\kappa(\cA)$ is a \emph{number} (the leading scalar curvature,
analogous to the first Chern class);
$\Delta_\cA(x)$ is a \emph{polynomial} (encoding a finite
spectrum of branch points, analogous to the Chern character);
$\mathfrak{R}^{\mathrm{mod}}_4(\cA)$ is a \emph{cohomology
class} (the first invariant that sees nonlinear OPE interaction
beyond the spectral data).  Together, they
seed the algebraicity theorem.

\medskip

\noindent\textbf{The scalar curvature $\kappa(\cA)$:}\enspace
the arity-two, genus-zero trace:
\[
\kappa(\cA)
\;=\;
\operatorname{tr}(\Theta_\cA)_{2,0}
\;=\;
\operatorname{tr}(\pi\circ m_2\circ\iota^{\otimes 2}
\circ\Delta_{\mathrm{sep}})
\;\in\;\Bbbk.
\]
This is the first Chern class of the modular bar bundle:
$\operatorname{obs}_g(\cA)=
\kappa(\cA)\cdot\lambda_g$, where $\lambda_g$ is the Hodge
class on~$\overline{\cM}_g$.  The Mumford relation
$\lambda_g^{g+1}=0$ confines genus-$g$ scalar obstructions to a space of dimension at most~$g$.

Explicit values across the standard landscape:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lccl}
\textbf{Algebra $\cA$}
  & $\kappa(\cA)$
  & $\kappa(\cA^!)$
  & \textbf{Sum rule}\\
\hline
Heisenberg $\cH_k$ & $k$ & $-k$ & $0$\\[2pt]
Affine $\widehat{\fg}_k$
  & $\dfrac{(k+h^\vee)\dim\fg}{2h^\vee}$
  & $-\dfrac{(k+h^\vee)\dim\fg}{2h^\vee}$ & $0$\\[6pt]
Virasoro $\mathrm{Vir}_c$ & $c/2$ & $(26-c)/2$ & $13$\\[2pt]
$\beta\gamma$ system & $1$ & $-1$ & $0$\\[2pt]
Lattice $V_\Lambda$ & $\operatorname{rank}(\Lambda)$
  & $-\operatorname{rank}(\Lambda)$ & $0$\\[2pt]
$\mathcal W_N(\widehat{\mathfrak{sl}}_N)$
  & $c\cdot(H_N{-}1)$
  & $c'\cdot(H_N{-}1)$
  & $K_N\cdot(H_N{-}1)$\\[6pt]
Free fermion $\psi$ & $1/4$ & $-1/4$ & $0$
\end{tabular}
\end{center}
The complementarity sum rule $\kappa(\cA)+\kappa(\cA^!)=0$ holds for
Kac--Moody algebras, free fields, and lattice vertex algebras.
For $\mathcal W$-algebras the sum is a nonzero constant
determined by the anomaly ratio: $\kappa(\mathrm{Vir}_c)+
\kappa(\mathrm{Vir}_{26-c})=13$, and
$\kappa(\mathcal W_{N,c})+\kappa(\mathcal W_{N,c'})
=K_N\cdot(H_N{-}1)$ where $K_N=c+c'$ is the family constant.
Self-duality occurs at $c=13$ for Virasoro and
$c=50$ for~$\mathcal W_3$.

\medskip

\noindent\textbf{The spectral discriminant $\Delta_\cA(x)$
and the branch transport operator.}

The second characteristic invariant is the
characteristic polynomial of a finite-rank operator.  The Koszul dual Hilbert series
\[
h_{\cA^!}(q)
\;=\;
\sum_{n\ge 0}\dim H^n(\barB(\cA))\,q^n,
\]
records bar cohomology dimensions.  For every standard family, $h_{\cA^!}(q)$ is a
\emph{rational} function: it satisfies a holonomic recurrence relation
of finite order~$d$, and the transfer matrix of this recurrence is
a $d\times d$ matrix $T_{\mathrm{rec}}$.

Define the \emph{spectral branch object} to be a finite-rank perfect
complex $V^{\mathrm{br}}_\cA$ together with a \emph{branch transport
operator} $T_{\mathrm{br},\cA}\colon
V^{\mathrm{br}}_\cA\to V^{\mathrm{br}}_\cA$ such that
\begin{equation}\label{eq:pref-delta-def}
\Delta_\cA(x)
\;:=\;
\operatorname{sdet}\!\bigl(1-x\,T_{\mathrm{br},\cA}\bigr).
\end{equation}
The rank of $V^{\mathrm{br}}_\cA$ equals the degree of algebraicity
of~$h_{\cA^!}(q)$: the order of the minimal recurrence.  The
eigenvalues of $T_{\mathrm{br},\cA}$ are the reciprocal branch
points of the analytic continuation of~$h_{\cA^!}$.

Three structural properties:
\begin{enumerate}[label=(\roman*)]
\item $\Delta_{\cA^!}(x)=\Delta_\cA(x)$: the spectral
  discriminant is \emph{self-dual}, unlike~$\kappa$ which is
  anti-symmetric for KM/free fields ($\kappa + \kappa' = 0$).
\item Exact factorization functors preserving quadratic OPE data
  preserve~$T_{\mathrm{br},\cA}$.
\item The spectral radius
  $\rho(T_{\mathrm{br},\cA})=\max_i|\lambda_i|$ equals
  $\dim\mathfrak g$ for affine Kac--Moody at generic level.
\end{enumerate}

\emph{Example: $\mathfrak{sl}_3$.}  The Koszul dual Hilbert series
of $\widehat{\mathfrak{sl}}_3$ satisfies a degree-$3$ recurrence.
The transfer matrix is $3\times 3$ with eigenvalues $8$,
$(3+\sqrt{13})/2$, $(3-\sqrt{13})/2$.  The spectral discriminant is
\[
\Delta_{\widehat{\mathfrak{sl}}_3}(x)
\;=\;
(1-8x)(1-3x-x^2).
\]
The dominant eigenvalue $8=\dim(\mathfrak{sl}_3)$ controls the
exponential growth of bar cohomology dimensions.  The remaining
eigenvalues $(3\pm\sqrt{13})/2$ are the roots of the DS
discriminant factor, shared with the $\mathcal W_3$ generating
function.

\emph{Example: Heisenberg.}  The Hilbert series
$h_{\mathcal H_k^!}(q)=1+q$ is a polynomial (the recurrence has
order~$0$ after the first term), so
$\Delta_{\mathcal H_k}(x)=1$: there is no non-scalar
structure.  This is the Gaussian archetype: $\kappa$ alone
determines everything.

\emph{Example: $\beta\gamma$.}  The Hilbert series is
$\sqrt{(1{+}q)/(1{-}3q)}$; the discriminant is
$\Delta_{\beta\gamma}(x)=(1-3x)(1+x)$.  The two roots at
$x=1/3$ and $x=-1$ coincide with $\widehat{\mathfrak{sl}}_2$
and the Virasoro algebra.

In the Chern--Weil dictionary, $\Delta_\cA$ plays the role of the
Chern character: the logarithmic derivative
\[
\operatorname{ch}_r(\cA)
\;=\;
\frac{1}{r!}\,
\frac{d^r}{dt^r}\Big|_{t=0}\bigl[-\log\Delta_\cA(t)\bigr]
\;=\;
\frac{1}{r}\operatorname{tr}(T_{\mathrm{br},\cA}^r)
\]
recovers the power-sum symmetric functions of the eigenvalues.

\medskip

\noindent\textbf{The quartic shadow
$\mathfrak R^{\mathrm{mod}}_{4,g,n}(\cA)$:}
\[
\mathfrak R^{\mathrm{mod}}_{4,g,n}(\cA)
\;=\;
\operatorname{pr}_{4,g,n}(\Theta_\cA)
\;\in\;
H^*(\overline{\cM}_{g,n})\otimes
(\bar\cA^{\vee})^{\otimes n}_{\mathrm{cyc}}.
\]
This is the first \emph{nonlinear} characteristic class: the first
invariant that cannot be recovered from~$\kappa$ and~$\Delta_\cA$.
Its genus-zero, four-point specialisation is the quartic contact
invariant $Q^{\mathrm{contact}}(\cA)$.  Explicit:
\[
Q^{\mathrm{contact}}_{\mathrm{Vir}}
\;=\;
\frac{10}{c(5c+22)},
\qquad
Q^{\mathrm{contact}}_{\cH}=0,
\qquad
Q^{\mathrm{contact}}_{\beta\gamma}
\;\neq\; 0.
\]
For Heisenberg, the quartic vanishes (no cubic OPE pole).
For $\beta\gamma$, the quartic is the first gauge-nontrivial
shadow (the cubic is gauge-removable by
Theorem~\ref{thm:cubic-gauge-triviality}).  For Virasoro, both cubic and
quartic are nonvanishing.

\subsection*{5.4.\enspace The Chern--Weil dictionary}

The analogy between $\Theta_\cA$ and a connection $1$-form is
exact.  The modular bar bundle
$\mathrm{B}^{\log}_{\mathrm{mod}}(\cA)\to\overline{\cM}_{g,n}$
is a principal bundle for the gauge group of the convolution
algebra; $\Theta_\cA$ is its flat connection (flatness automatic
from the bar-intrinsic construction); and the shadow
tower is its Chern--Weil theory.  Holonomy becomes factorisation
homology, gauge equivalence becomes MC gauge, and the Weil
homomorphism becomes the shadow algebra
$\cA^{\mathrm{sh}} = H_\bullet(\Defcyc^{\mathrm{mod}})$.

\begin{center}
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{ll}
\textbf{Classical Chern--Weil}
  & \textbf{Modular factorization}\\
\hline
Principal $G$-bundle $P\to M$
  & Modular bar bundle
    $\mathrm{B}^{\log}_{\mathrm{mod}}(\cA)\to\overline{\cM}_{g,n}$\\[2pt]
Connection $1$-form $\omega\in\Omega^1(P,\fg)$
  & MC element $\Theta_\cA\in\mathrm{MC}(\gAmod)$\\[2pt]
Curvature $\Omega=d\omega+\frac{1}{2}[\omega,\omega]$
  & MC equation $D\Theta_\cA+\tfrac12[\Theta_\cA,\Theta_\cA]=0$\\[2pt]
Flatness $\Omega=0$
  & Automatic (bar-intrinsic)\\[2pt]
First Chern class $c_1\in H^2(M;\mathbb Z)$
  & Scalar curvature $\kappa(\cA)=\operatorname{tr}(\Theta_\cA)_{2,0}$\\[2pt]
Chern character $\operatorname{ch}=\operatorname{tr}\exp(\Omega/2\pi i)$
  & Spectral determinant
    $\Delta_\cA(t)=\operatorname{sdet}(1-tH_{d_\Theta})$\\[2pt]
Higher Chern classes $c_r$
  & Shadows $\mathfrak R^{\mathrm{mod}}_{4,g,n}$,
    $\mathrm{Sh}_r$ for $r\ge 5$\\[2pt]
Weil homomorphism $W\colon\operatorname{Sym}^*(\fg^*)^G\to H^*(M)$
  & Shadow algebra
    $\cA^{\mathrm{sh}}=H_\bullet(\Defcyc^{\mathrm{mod}})$\\[2pt]
$\operatorname{ad}$-invariant polynomial
  & Cyclic cocycle in $\Defcyc^{\mathrm{mod}}(\cA)$\\[2pt]
Cyclic pairing $\operatorname{tr}(XY)$
  & Verdier duality on $\operatorname{Ran}(X)$\\[2pt]
Group multiplication $G\times G\to G$
  & Operadic composition in $\cP^{\mathrm{ch}}$\\[2pt]
Coproduct on $\cO(G)$
  & Operadic cocomposition / clutching / degeneration\\[2pt]
Lagrangian splitting $T^*G=\fg\oplus\fg^*$
  & Complementarity $Q_g(\cA)\oplus Q_g(\cA^!)
    =H^*(\overline{\cM}_g,\mathcal Z(\cA))$\\[2pt]
Holonomy $\operatorname{Hol}(\gamma)\in G$
  & Factorisation homology $\int_\Sigma\cA$\\[2pt]
Gauge equivalence $\omega\sim g^{-1}\omega g+g^{-1}dg$
  & MC gauge in
    $\mathrm{MC}_\bullet(\gAmod)$\\[2pt]
Transgression $\mathrm{CS}(\omega)\in\Omega^3$
  & Shadow Postnikov obstruction tower (Section~6)\\[2pt]
Flat sections $\nabla s=0$
  & Twisted cochains $d_{\Theta_\cA}(x)=0$
\end{tabular}
\end{center}

\subsection*{5.5.\enspace The genus spectral sequence}

The genus filtration $F^g L_{\mathrm{mod}}:=\bigoplus_{g'\ge g}
(\gAmod)_{g',*,*}$ yields a convergent spectral sequence.  Write
$D_0=D_{\mathrm{int}}+D_{\mathrm{sep}}$ for the genus-preserving
part of the differential and $D_1=D_{\mathrm{nsep}}$ for the
genus-raising part.  These satisfy $D_0^2=0$,
$D_0D_1+D_1D_0=0$, $D_1^2=0$ (a bicomplex structure).

The spectral sequence:
\begin{enumerate}[label=(\roman*)]
\item $E_0^{p,q}=\operatorname{gr}_F^p L_{\mathrm{mod}}^{p+q}$
  with differential $d_0=[D_0,-]$.
\item $E_1^{p,*}=H^*(\operatorname{gr}_F^p L_{\mathrm{mod}},d_0)$:
  the associated graded cohomology, genus by genus.  $p=0$:
  tree-level (unlooped homotopy transfer).  $p=1$:
  one-loop (BV trace and deformations).  $p=2$:
  genus-two shells (loops, clutching, planted forests).
\item $d_1\colon E_1^{0,*}\to E_1^{1,*}$ is the genus-one
  obstruction $\operatorname{Ob}_1$: the obstruction to lifting a
  tree-level MC element to one-loop.  More generally,
  $d_r\colon E_r^{p,*}\to E_r^{p+r,*-r+1}$ encodes
  $\operatorname{Ob}_r$.
\item $E_\infty^{p,q}\cong\operatorname{gr}_F^p H^{p+q}
  (L_{\mathrm{mod}})$: the associated graded of the full modular
  cohomology.
\end{enumerate}
Convergence follows from completeness of the depth filtration and
pronilpotence of the weight filtration: the
$\varprojlim^1$ term vanishes by Mittag-Leffler
(finite-dimensionality in each conformal weight).

This spectral sequence is \emph{distinct} from the PBW spectral
sequence (which decomposes by conformal weight within a fixed genus).
PBW computes \emph{what} bar cohomology is;
the genus spectral sequence determines \emph{whether} the MC element
extends across genera.  For Heisenberg, it
degenerates at $E_1$.  For Virasoro,
$d_1\neq 0$ and nontrivial differentials persist at every page.

\subsection*{5.6.\enspace Homotopy invariance and functoriality}

The shadow algebra
$\cA^{\mathrm{sh}}=H_\bullet(\Defcyc^{\mathrm{mod}}(\cA))$ is a
homotopy invariant of the chiral algebra.  For any
$\infty_\alpha$-quasi-isomorphism
$f\colon\cA\xrightarrow{\sim}\cA'$, the induced map on MC
$\infty$-groupoids
\[
f_*\colon
\operatorname{MC}_\bullet(\gAmod)
\;\xrightarrow{\;\sim\;}
\operatorname{MC}_\bullet(\mathfrak g^{\mathrm{mod}}_{\cA'})
\]
is a weak homotopy equivalence (a quasi-isomorphism on tangent
complexes at corresponding MC elements).  In particular:
\begin{itemize}
\item The scalar $\kappa(\cA)$ is a quasi-isomorphism invariant.
\item The spectral determinant $\Delta_\cA(t)$ is a
  quasi-isomorphism invariant.
\item The full shadow obstruction tower
  $(\kappa,\Delta,\mathfrak C,\mathfrak Q,\mathrm{Sh}_5,
  \mathrm{Sh}_6,\dots)$ consists of quasi-isomorphism invariants.
\item The MC element $\Theta_\cA$ is a quasi-isomorphism invariant
  up to gauge: $f_*(\Theta_\cA)$ and $\Theta_{\cA'}$ are
  gauge-equivalent in $\mathrm{MC}_\bullet(\mathfrak
  g^{\mathrm{mod}}_{\cA'})$.
\end{itemize}

The assignment
$\cA\mapsto(\gAmod,\Theta_\cA)$ is a functor from
chiral algebras (with $\infty_\alpha$-quasi-isos
inverted) to MC moduli problems:
modular Koszul duality is a derived invariant.

The convolution $L_\infty$ algebra
$\Convinf(\cC,\cP)$ is functorial in each slot separately, but
\emph{not} simultaneously as a bifunctor (\S3).  Functoriality of
$\cA\mapsto\gAmod$ proceeds through the source slot,
with the target operad held fixed.

\subsection*{5.7.\enspace The shadow CohFT and topological recursion}

Projected
to $\overline{\cM}_{g,n}$, the MC equation produces
tautological classes and tautological relations.
The MC element $\Theta_\cA$ determines shadow tautological classes
$\tau_{g,n}(\cA)\in R^*(\overline{\cM}_{g,n+1})$
that assemble into a cohomological field theory
(Theorem~\ref{thm:shadow-cohft}):
the factorisation axiom holds by the clutching law
for~$\Theta_\cA$, the $\Sigma_n$-equivariance by the symmetry of
stable-graph summation, and the flat identity conditionally (when
the vacuum lies in~$V$).

Projecting the MC equation
$D\Theta_\cA+\tfrac12[\Theta_\cA,\Theta_\cA]=0$ to the
$(g,n)$-component yields a tautological relation in
$R^*(\overline{\cM}_{g,n})$ at each $(g,n)$
(Theorem~\ref{thm:mc-tautological-descent}):
\[
\sum_{\mathrm{sep}/\mathrm{nsep}}
\xi_{\mathrm{sep},*}\bigl(
\tau_{g_1,|S|}(\cA)\cdot\tau_{g_2,|S^c|}(\cA)\bigr)
+\delta_{\mathrm{pf}}^{(g,n)}
\;=\;0.
\]

\medskip

\noindent\textbf{WDVV and Mumford from MC.}\enspace
At genus~$0$, arity~$3$: the MC tautological relation on
$\overline{\cM}_{0,4}$ reduces to the WDVV equations
(Proposition~\ref{prop:wdvv-from-mc}).  At arity~$2$,
genus~$g\geq 2$: substituting
$\tau_{g,2}(\cA)=\kappa(\cA)\cdot\pi^*\lambda_g$ recovers
the Mumford $\lambda$-class clutching relation on
$\overline{\cM}_g$
(Proposition~\ref{prop:mumford-from-mc}).

The complementarity propagator
$P_\cA\colon H^*(\cA)\otimes H^*(\cA^!)\to\mathbb C$
is the Givental $R$-matrix of the shadow CohFT; when
it carries a flat unit (all standard families
with vacuum in~$V$; Theorem~\ref{thm:shadow-cohft}),
Teleman reconstruction recovers $\{\tau_{g,n}\}$
at all $(g,n)$ from genus-$0$ data and~$P_\cA$
(Theorem~\ref{thm:cohft-reconstruction}).  Eynard--Orantin
topological recursion is the MC equation applied to the shadow obstruction tower
(Corollary~\ref{cor:topological-recursion-mc-shadow}).

\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{ll}
\textbf{MC datum} & \textbf{Tautological output} \\ \hline
$\Theta_\cA\in\mathrm{MC}(\gAmod)$
  & shadow CohFT $\Omega_{g,n}^\cA$ \\[2pt]
$D^2=0$ on $\mathrm{FM}^{\log}$
  & CohFT axioms \\[2pt]
$D\Theta+\tfrac12[\Theta,\Theta]=0$ at $(g,n)$
  & tautological relation \\[2pt]
$[\Theta,\Theta]|_{\mathrm{sep}}$
  & WDVV / associativity \\[2pt]
$\hbar\Delta(\Theta)|_{\mathrm{nsep}}$
  & Mumford $\lambda$-class relations \\[2pt]
$P_\cA$
  & Givental $R$-matrix \\[2pt]
MC recursion
  & EO topological recursion
\end{tabular}
\end{center}

\medskip
\noindent\textbf{The Pixton shadow bridge.}\enspace
For class-M algebras (infinite shadow obstruction tower), $\Theta_\cA$ generates tautological classes at every genus.
At genus~$2$--$3$, the relations
$\tau_{g,n}(\mathrm{Vir}_c)$ for generic~$c$ produce elements of the
Pixton ideal in~$R^*(\overline{\cM}_{g,n})$: Pixton's tautological ring
relations arise as shadows of the Virasoro MC
equation.  Conjecture~\ref{conj:pixton-from-shadows}: class-M algebras
generate the Pixton ideal via the infinite MC tower.  Computationally
supported at genus~$2$--$3$; formal ideal membership
in the strata algebra is open.

\medskip
\noindent\textbf{The B\"ocherer bridge.}\enspace
At genus~$2$, the shadow tautological class
$\tau_{2,0}(\mathrm{Vir}_c)$ for lattice vertex algebras computes a
central $L$-value via the B\"ocherer conjecture (now a theorem of
Furusawa--Morimoto).  For the Leech lattice:
$\chi_{12}=\mathrm{SK}(f_{22})$ (the Saito--Kurokawa lift of the
unique weight-$22$ cuspidal eigenform), and the MC-derived second
Fourier coefficient $c_2\approx -1.918\times 10^{-6}\neq 0$ is the
first nonzero central $L$-value produced by the shadow obstruction tower.

\subsection*{5.8.\enspace The primitive kernel and cofree reduction}

The MC element $\Theta_\cA$ lives in the cofree
conilpotent coalgebra underlying the modular bar construction.
By Milnor--Moore for modular operads, $\Theta_\cA$
is determined by its restriction to primitive
corollas and rigid cutting strata, the \emph{primitive
logarithmic modular kernel}
\[
\mathfrak K_\cA
\;=\;
\sum_{g\geq 0,\,n\geq 2}K_{g,n}^\cA
+\sum_{\rho\in\mathrm{Rig}}K_\rho^\cA,
\]
where $K_{g,n}^\cA$ are genus-$g$ corolla coefficients and
$K_\rho^\cA$ are rigid boundary cutting terms.
The fundamental equivalence
(Theorem~\ref{thm:primitive-to-global-reconstruction}):
\[
(Q_\cA^{\mathrm{mod}})^2=0
\quad\iff\quad
d\,\mathfrak K_\cA+\mathfrak K_\cA\star\mathfrak K_\cA
+\hbar\,\Delta_{\mathrm{ns}}(\mathfrak K_\cA)=0,
\]
where $\star$ is the primitive pre-Lie product from log-FM
residues, replaces the genus-by-genus obstruction programme
by a single equation on primitive data.

\medskip

\noindent\textbf{Shell equations.}\enspace
Projecting the primitive master equation to genus~$2$ and
genus~$3$ shells gives explicit constraints:
\begin{align*}
R_2(\mathfrak K_\cA)
&=\Delta_{\mathrm{ns}}(K_1)
  +\tfrac12[K_1,K_1]
  +\textstyle\sum_{\rho\in\mathrm{Rig}_2}R_\rho^\cA(K_{0,2}^\cA),\\
R_3(\mathfrak K_\cA)
&=\Delta_{\mathrm{ns}}(K_2)
  +[K_1,K_2]
  +\tfrac{1}{3!}\ell_3(K_1,K_1,K_1)
  +\textstyle\sum_\rho R_\rho^\cA(\ldots).
\end{align*}
For the Heisenberg algebra, only the BV term
$\Delta_{\mathrm{ns}}$ survives.  For affine Kac--Moody,
the bracket $[K_1,K_1]$ contributes the cubic shadow.  For
$\beta\gamma$, cubic gauge triviality kills the bracket term
and the rigid stratum contributes the quartic contact
invariant.  For Virasoro and $\mathcal W_N$, all three terms
are active at every genus.

\medskip

\noindent\textbf{The branch BV action.}\enspace
The finite-rank branch-active quotient
$V_\cA^{\mathrm{br}}=V_\cA^+\oplus V_\cA^-$, a
quotient of the modular tangent complex,
spanned by spectral generators, carries a BV master action
\[
S_\cA^{\mathrm{br}}(x,\xi)
=\tfrac12\Omega_\cA(K_\cA^{\mathrm{br}}x,x)
+\sum_{m+n\geq 3}
\frac{1}{m!\,n!}\mu_{m,n}^\cA(x^{\otimes m};\xi^{\otimes n}),
\]
satisfying
$\hbar\,\Delta_\cA^{\mathrm{br}}S_\cA^{\mathrm{br}}
+\tfrac12\{S_\cA^{\mathrm{br}},S_\cA^{\mathrm{br}}\}_{\mathrm{BV}}
=0$,
where $\{-,-\}_{\mathrm{BV}}$ is the odd Poisson bracket
induced by the invariant pairing on~$\cA$.
The \emph{metaplectic half-density}
$\delta_\cA\in 1+x\,\Bbbk\llbracket x\rrbracket$ satisfies
$\delta_\cA^2=\Delta_\cA=\det(1-x\,T_\cA^{\mathrm{br,red}})$:
the spectral discriminant is the square of a canonical
half-density.

\subsection*{5.9.\enspace Entanglement from the modular characteristic}

The bar coalgebra carries a natural bipartite structure: its
coproduct splits a configuration of points into two halves, one on
each side of a spatial cut.  This splitting connects the modular
characteristic directly to entanglement.

For a
spatial bipartition of an interval of length~$L$ with UV
cutoff~$\varepsilon$, the scalar projection of $\Theta_\cA$
restricted to the bipartite cut yields the
Ryu--Takayanagi formula:
\[
S_{\mathrm{EE}}(\cA)
\;=\;
\frac{c(\cA)}{3}\log\frac{L}{\varepsilon},
\]
where $c(\cA)$ is the central charge.
(For the Virasoro algebra, $c=2\kappa$; the relationship between
$c$ and~$\kappa$ is family-dependent.)
Complementarity gives the entanglement sum rule:
\[
S_{\mathrm{EE}}(\cA)+S_{\mathrm{EE}}(\cA^!)
\;=\;
\frac{c(\cA)+c(\cA^!)}{3}\cdot\log\frac{L}{\varepsilon}.
\]
For the Virasoro family $\mathrm{Vir}_c^!=\mathrm{Vir}_{26-c}$,
this gives $c+c'=26$ and the universal sum~$26/3\cdot\log(L/\varepsilon)$.

The four shadow-depth classes (G/L/C/M) classify entanglement
complexity: class~G algebras (Gaussian, $r_{\max}=2$) exhibit
area-law entanglement only; class~L ($r_{\max}=3$) adds subleading
logarithmic corrections from the cubic shadow; class~C
($r_{\max}=4$) adds a contact correction from the quartic
invariant; and class~M ($r_{\max}=\infty$) carries an infinite tower
of entanglement corrections, one for each shadow.

\medskip
\noindent\textbf{The entanglement programme (G11--G16).}\enspace
Six theorem targets extend the scalar result.
\emph{G11}: the Ryu--Takayanagi formula above, proved from the
scalar projection of~$\Theta_\cA$.
\emph{G12} (Koszulness $=$ exact quantum error correction): the
Knill--Laflamme condition for quantum error correction is the
Lagrangian isotropy condition from the complementarity pairing;
shadow depth~$r_{\max}$ equals the number of redundancy channels;
the twelve Koszulness characterizations (K1--K12; ten
unconditional equivalences, one conditional, one
one-directional) translate into a
twelve-fold code dictionary; failure of Koszulness is failure of
the code.
\emph{G13}: the replica trick from the MC equation (the
$n$-sheeted cover computation is the $n$-fold bar coproduct).
\emph{G14}: modular flow from the tangent complex (the Tomita
modular operator is the $L_\infty$-twisted differential
$d_{\Theta_\cA}$, restricted to the bipartite subalgebra).
\emph{G15}: the quantum extremal surface as the shadow
connection Ward identity: the QES equation is the stationarity
condition for the shadow metric~$Q_L(t)$ restricted to the
entanglement cut.
\emph{G16}: the Page curve from the shadow connection at $c = 13$
(the self-dual point): the Page transition occurs when the
shadow growth rate~$\rho(\cA)$ crosses the entanglement
threshold, and the scrambling time is controlled by the
spectral discriminant~$\Delta_\cA$.

% ====================================================================
\section*{6.\quad The shadow obstruction tower}
% ====================================================================

\subsection*{6.1.\enspace The extension tower}

Can $\Theta_\cA$ be approximated by finitely many
arities, and what controls the passage from one finite
approximation to the next?  The total weight
filtration answers both.

Define the \emph{total weight} $w(g,r,d):=2g-2+r+d$, where $g$ is
loop genus, $r$ is arity, and $d$ is log boundary depth.  The total
weight filtration $F^N\mathfrak{g}^{\mathrm{amb}}_\cA:=\bigoplus_{w\ge N}(\mathfrak{g}^{\mathrm{amb}}_\cA)_{g,r,d}$
is an exhaustive, separated, complete filtration.  Here
$\mathfrak g^{\mathrm{amb}}_\cA$ denotes the \emph{ambient}
(planted-forest-extended) modular convolution algebra, the
extension of $\gAmod$ by the planted-forest coefficient algebra
$\mathcal G_{\mathrm{pf}}$ that incorporates log boundary
strata.  The \emph{modular extension tower}:
\[
\cE_\cA(N)
:=\operatorname{MC}\bigl(\mathfrak g^{\mathrm{amb}}_\cA/F^{N+1}\bigr),
\qquad N\ge 1.
\]
Restriction maps
$\cE_\cA(N+1)\to\cE_\cA(N)$ truncate the top weight.  A
\emph{full lift} is a compatible point of the inverse system:
\[
\Theta_\cA\;\in\;
\varprojlim_{N}\,\cE_\cA(N).
\]
The bar-intrinsic construction provides such a point
unconditionally.  The shadow obstruction tower is the study of the
extension tower $\cE_\cA(1)\leftarrow
\cE_\cA(2)\leftarrow\cE_\cA(3)\leftarrow\cdots$ and the
obstructions that arise at each stage.

\subsection*{6.2.\enspace Obstruction classes and the all-arity master equation}

Define the truncated MC elements $\Theta_\cA^{\le r}$ by projecting
$\Theta_\cA$ to total weight $\le r$.  The \emph{shadow obstruction
tower} is the sequence
\[
\Theta_\cA^{\le 2},\quad
\Theta_\cA^{\le 3},\quad
\Theta_\cA^{\le 4},\quad
\Theta_\cA^{\le 5},\quad\dots
\]
At each truncation, the MC equation fails by a remainder:
\[
D\Theta^{\le r}_\cA
+\tfrac12[\Theta^{\le r}_\cA,\Theta^{\le r}_\cA]
\;=\;
-o_{r+1}(\cA),
\]
where the \emph{obstruction class} $o_{r+1}(\cA)$ lives in the
$(r+1)$-graded piece:
\[
o_{r+1}(\cA)
\;\in\;
Z^2\!\left(\frac{F^{r+1}\mathfrak g^{\mathrm{amb}}_\cA}
{F^{r+2}\mathfrak g^{\mathrm{amb}}_\cA},\;d_{\le r}\right).
\]
The truncation extends to
$\Theta^{\le r+1}$ if and only if $[o_{r+1}(\cA)]=0$ in
$H^2(F^{r+1}/F^{r+2},d_{\le r})$.  The bar-intrinsic
construction guarantees that extension always exists, so
the obstruction class is always exact; the shadow obstruction tower
records the gauge choices at each stage.

The all-arity master equation at arity~$r$ is:
\[
\nabla_H(\mathrm{Sh}_r(\cA))+o^{(r)}(\cA)=0,
\qquad r\ge 3,
\]
where $\nabla_H$ is the Hodge covariant derivative (the linearised
MC operator twisted by the previous stages) and $\mathrm{Sh}_r(\cA)$
is the arity-$r$ shadow (the named invariant extracted from
$\Theta^{\le r}$).  This equation determines $\mathrm{Sh}_r$
uniquely modulo gauge if $H^1(F^r/F^{r+1},d_{\le r-1})=0$, and
up to the image of a gauge map otherwise.

\subsection*{6.3.\enspace Cubic gauge triviality and the canonical quartic}

\begin{quote}
\textbf{Cubic gauge triviality.}\enspace
When $H^1(F^3\mathfrak g/F^4\mathfrak g,\,d_2)=0$, the cubic MC
term $\Theta^{[3]}_\cA$ is gauge-trivial: there exists a gauge
transformation $\exp(\xi_3)$ with $\xi_3\in F^3$ such that
$\exp(\xi_3)\cdot\Theta^{\le 3}_\cA$ has vanishing weight-$3$
component.
\end{quote}

After this gauge transformation, the quartic obstruction class
$[\mathfrak Q(\cA)]\in H^2(F^4\mathfrak g/F^5\mathfrak g,\,d_2)$
is \emph{canonical}: independent of homotopy
retraction data, cubic gauge, and MC gauge orbit representative.
This is the first characteristic class
not polynomial in~$\kappa$.

The mechanism is standard Postnikov:
$o_3(\cA)\in H^2(F^3/F^4,d_2)$ is exact (since
$\Theta_\cA$ exists), and the cochain $\Theta^{[3]}$
lifting it is unique up to coboundary when
$H^1(F^3/F^4,d_2)=0$.  After removal, the quartic error is a
well-defined cohomology class: trivial $H^1$ at level~$n$ makes the $H^2$ class at
level~$n+1$ canonical.

The clutching law for the quartic class follows from Mok's log
FM degeneration formula.  For a degeneration
$C\leadsto C_0=C_1\cup_p C_2$:
\[
\mathfrak Q(\cA)\big|_{C_0}
\;=\;
\sum_{a+b=4}\mathfrak Q^{(a)}(\cA)\big|_{C_1}
\cdot\mathfrak Q^{(b)}(\cA)\big|_{C_2}
\;+\;
\text{planted-forest correction}.
\]
The planted-forest correction is genuinely logarithmic,
with no counterpart in the classical Deligne--Mumford setting.

The quartic contact invariant:
\[
Q^{\mathrm{contact}}_{\mathrm{Vir}}
\;=\;
\frac{10}{c(5c+22)}
\;\in\;
H^2(F^4/F^5,d_2).
\]
The denominator $c(5c+22)$ has physical meaning: $c=0$ is the
logarithmic threshold; $c=-22/5$ is the minimal model accumulation
point $\mathcal M(2,5)$.  The numerator~$10=\binom{5}{2}$ counts
the arity-four Catalan channels.


\subsection*{6.4.\enspace The Hamilton--Jacobi generating function}

For a multi-generator algebra ($\mathcal{W}_3$ with
generators $T$ (weight~$2$) and $W$ (weight~$3$)), the
deformation space is two-dimensional.  The Riccati ODE lifts
to a Hamilton--Jacobi PDE.  Write
$U=\sum_{s\ge 3}\mathrm{Sh}_s(x_T,x_W)$.  The master equation
becomes
\[
2\,E(U)+\tfrac{1}{2}\lVert\nabla U\rVert^2_H
\;=\;R(x_T,x_W),
\]
with Euler operator $E=x_T\partial_T+x_W\partial_W$,
kinetic energy
$\lVert\nabla U\rVert^2_H
=(2/c)(\partial_T U)^2+(3/c)(\partial_W U)^2$,
and $R$ a polynomial of degree~$\le 4$ encoding the
three inputs $(\kappa,\mathfrak{C},\mathfrak{Q})$.
The gradient
$dU\colon X\to T^*X$ embeds the deformation space as a
Lagrangian submanifold of $T^*X$
($X = \bC\cdot x_T\oplus\bC\cdot x_W$,
kinetic form positive-definite for $c>0$),
by the Hamilton--Jacobi theorem applied to the stationary
equation with Euler operator~$E$ as
arity-filtration weight.  Whether the genus expansion
$\Theta_\cA = \sum_{g \geq 0}\hbar^g\Theta_\cA^{(g)}$
admits a quantisation in which $U$ is the leading
semiclassical term is an open problem: it would require
constructing a quantum Hamiltonian whose WKB expansion
has leading term~$U$ and whose quantum corrections
reproduce the genus-$g$ shadow amplitudes.

On the $T$-line ($x_W=0$): conformal weight forces the
transverse momentum $p_W=(\partial_W U)|_{x_W=0}$ to vanish,
and the Hamilton--Jacobi PDE collapses to the Riccati ODE.
On the $W$-line ($x_T=0$): the cubic shadow
$\mathrm{Sh}_3 = 2x_T^3 + 3x_T x_W^2$
has nonzero normal derivative
$(\partial_T\mathrm{Sh}_3)|_{x_T=0}=3x_W^2$,
so the transverse kinetic energy is nonzero.  The first
inter-channel coupling correction enters at arity~$6$:
\[
\delta_6^{W\text{-line}}
\;=\;
\frac{576(5c+38)}{c^3(5c+22)^3}.
\]
The $T$-line is autonomous; the $W$-line is not.  The
asymmetry is intrinsic: it traces to the conformal-weight
asymmetry between $T$ (weight~$2$) and $W$ (weight~$3$).

\subsection*{6.5.\enspace The four depth classes}

The \emph{shadow depth} $r_{\max}(\cA)$ is the smallest integer~$r$
such that $o_{r+1}(\cA)=0$ for all subsequent levels, or
$r_{\max}=\infty$ if the tower never terminates.  Equivalently,
$r_{\max}$ is the largest arity at which the shadow obstruction tower carries a
nontrivial invariant.

The standard landscape partitions into exactly four depth classes;
no other values occur on any one-dimensional primary
slice.  The single-line dichotomy
(Theorem~\ref{thm:single-line-dichotomy}): the shadow metric
$Q_L(t)$ is quadratic in $(\kappa,\alpha,S_4)$,
and its factorisation type (perfect square or
irreducible) determines whether the tower terminates.

\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lcccll}
\textbf{Class} & \textbf{Symbol} & $r_{\max}$
  & $\ell_3^{(0)},\;\ell_4^{(0)}$
  & \textbf{Potential type} & \textbf{Examples}\\
\hline
Gaussian & G & $2$ & $0,\;0$
  & quadratic
  & Heisenberg $\cH_k$, free fermion $\psi$\\
Lie/tree & L & $3$ & $\neq 0,\;0$
  & cubic
  & Affine $\widehat{\mathfrak{sl}}_N$, current algebras\\
Contact & C & $4$ & $0,\;\neq 0$
  & quartic
  & $\beta\gamma$, $bc$ ghosts\\
Mixed & M & $\infty$ & $\neq 0,\;\neq 0$
  & non-polynomial
  & Virasoro, $\mathcal W_N$, $\mathcal W_\infty$
\end{tabular}
\end{center}

\noindent
The depth class is determined by the OPE structure:
\begin{itemize}
\item \textbf{Gaussian} ($r_{\max}=2$): the transferred brackets
  $\ell_k^{(0)}$ vanish for $k \ge 3$ on bar cohomology, so
  the tower terminates at~$\kappa$.  Two mechanisms:
  Heisenberg has no simple pole ($S_3 = 0$, no
  Lie bracket); the free fermion has a simple pole but
  fermionic antisymmetry forces $S_3 = 0$ (parity on three-point configuration space).
  Sewing is by Fredholm determinant
  (Heisenberg) or Pfaffian (fermion).
  The potential is quadratic.
\item \textbf{Lie/tree} ($r_{\max}=3$): the OPE has a simple pole
  generating a Lie bracket, but the transferred quaternary bracket
  $\ell_4^{(0)}$ vanishes on bar cohomology.  The ternary bracket
  is the last nontrivial shadow.  The potential is cubic.
\item \textbf{Contact} ($r_{\max}=4$): the simple-pole bracket
  vanishes on bar cohomology (as in Heisenberg), but the quaternary
  bracket survives.  The first nontrivial shadow is
  $\mathfrak Q(\cA)$, and the tower terminates there.
  The potential is quartic.
\item \textbf{Mixed} ($r_{\max}=\infty$): both cubic and quartic
  shadows are nontrivial, and their interaction (the Poisson bracket
  $\{\mathfrak C,\mathfrak Q\}_H$) generates a nonvanishing quintic
  obstruction, which in turn generates a sextic, and so on.  The
  tower never terminates.  The potential is transcendental.
\end{itemize}

\medskip

\noindent\textbf{Shadow depth is not Koszulness.}\enspace
All four depth classes contain chirally Koszul algebras.  Heisenberg
(depth~$2$), affine at generic level (depth~$3$), $\beta\gamma$
(depth~$4$), and Virasoro (depth~$\infty$) are all chirally Koszul.
Shadow depth classifies the \emph{complexity} of Koszul algebras,
not Koszulness itself.

The \emph{operadic complexity theorem}
(Theorem~\ref{conj:operadic-complexity-detailed}): the shadow depth
equals the $A_\infty$-depth equals the $L_\infty$-formality level:
\[
r_{\max}(\cA)
\;=\;
A_\infty\text{-depth}(\cA)
\;=\;
L_\infty\text{-formality level}(\cA).
\]
Here $A_\infty$-depth is the largest~$r$ with $m_r\neq 0$ in
the minimal $A_\infty$ model; $L_\infty$-formality
level is the largest~$r$ with a nontrivial $r$-ary bracket on bar
cohomology (not removable by
$L_\infty$-isomorphism).  The shadow obstruction tower equals
the $L_\infty$ formality obstruction tower at all
arities
(Theorem~\ref{thm:shadow-formality-identification}).

\subsection*{6.6.\enspace The genus--arity bigrading}

The MC equation decomposes along two orthogonal axes
(Remark~\ref{rem:two-orthogonal-axes}).  The \emph{genus axis}
extends $\Theta_\cA$ from genus~$0$ to~$1$ to~$2$,
controlled by the genus spectral sequence
(Construction~\ref{const:vol1-genus-spectral-sequence}).  The
\emph{arity axis} extends $\Theta_\cA^{\leq 2}$ to
$\Theta_\cA^{\leq 3}$ to $\Theta_\cA^{\leq 4}$,
controlled by cyclic obstruction classes.  At fixed arity~$2$
the genus tower is governed by~$\kappa$ alone; at fixed genus~$0$ each new shadow coefficient introduces
independent data.
The axes couple through the \emph{visibility formula}
(Corollary~\ref{cor:shadow-visibility-genus}):
$g_{\min}(S_r) = \lfloor r/2 \rfloor + 1$, so $S_r$ first
contributes at genus $\lfloor r/2 \rfloor + 1$ and two new shadow
coefficients enter at each genus.

\subsection*{6.7.\enspace Genus-two shells}

Genus~$2$ is the first level where all three boundary
strata interact.  The genus-two MC component
decomposes as:
\[
\Theta^{(2)}_\cA
\;=\;
\underbrace{\Theta^{(2)}_{\mathrm{loop}\circ\mathrm{loop}}}_{%
\text{iterated BV: two self-loops}}
\;+\;
\underbrace{\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}}_{%
\text{clutching $\times$ BV: one separating + one self-loop}}
\;+\;
\underbrace{\Theta^{(2)}_{\mathrm{pf}}}_{%
\text{planted-forest: Mok's log-FM strata}}.
\]

The iterated-BV term $\Theta^{(2)}_{\mathrm{loop}^2}$ involves the
graph with one vertex of genus~$0$ and two self-loops (the
``figure-eight'').  Its amplitude is the iterated trace:
\[
\Theta^{(2)}_{\mathrm{loop}^2}
\;=\;
\tfrac{1}{2}\operatorname{tr}_1\operatorname{tr}_2
\bigl(P_\cA^{\otimes 2}\circ m^{(h)}_{0,4}\circ\Delta^{\otimes 2}\bigr).
\]

The separating-times-loop term
$\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}$ is the graph with
two vertices connected by a separating edge, one vertex carrying a
self-loop.  Its amplitude is:
\[
\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}
\;=\;
\operatorname{tr}_{\mathrm{ns}}\bigl(
P_\cA\circ\ell_2^{(0)}(\Theta^{(1,\bullet)},\Theta^{(1,\bullet)})
\bigr).
\]

The planted-forest term is the genuinely logarithmic contribution,
present only when the algebra has nontrivial cubic or quartic
shadows.  It arises from depth-$2$ strata of
$\operatorname{FM}_n(X\mathbin{|}D)$ that have no classical
counterpart.

\medskip

\noindent
The family-by-family structure:

\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lcccc}
& $\Theta^{(2)}_{\mathrm{loop}^2}$
& $\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}$
& $\Theta^{(2)}_{\mathrm{pf}}$
& \textbf{Depth class}\\
\hline
\textbf{Heisenberg} $\cH_k$
  & $\checkmark$ & --- & --- & G\\
\textbf{Affine} $\widehat{\fg}_k$
  & $\checkmark$ & $\checkmark$ & --- & L\\
\textbf{$\beta\gamma$ system}
  & $\checkmark$ & --- & --- & C\\
\textbf{Virasoro} $\mathrm{Vir}_c$
  & $\checkmark$ & $\checkmark$ & $\checkmark$ & M\\
$\boldsymbol{\mathcal W_N}$
  & $\checkmark$ & $\checkmark$ & $\checkmark$ & M
\end{tabular}
\end{center}

For Heisenberg: only the iterated BV contributes (two independent
loop contractions on a free field).  No separating clutching (the Lie
bracket on bar cohomology is central) and no planted forests (no
higher interactions).  For affine: the separating-times-loop term
appears (the Lie bracket creates a nontrivial genus-one correction
after one clutching), but planted forests are absent (the cubic
shadow terminates the tower).  For Virasoro and $\mathcal W_N$: all
three terms contribute, and the planted-forest term carries the
quartic resonance data.  For $\beta\gamma$: both the separating and planted-forest terms
vanish: the separating term because the Lie bracket is trivial on
bar cohomology, the planted-forest term because the quartic contact
invariant $\mu_{\beta\gamma}=0$ (rank-one abelian rigidity).  Only
the iterated BV shell contributes, as for Heisenberg, but via
contact termination rather than Gaussian collapse.

\subsection*{6.8.\enspace The genus loop operator}

The \emph{genus loop operator}
$\Lambda_P\colon\operatorname{Sym}^r(\bar\cA^\vee)_{\mathrm{cyc}}
\to\operatorname{Sym}^{r-2}(\bar\cA^\vee)_{\mathrm{cyc}}$ contracts
two legs of an arity-$r$ cyclic cochain with the propagator:
\[
\Lambda_P(\phi)(a_1,\dots,a_{r-2})
\;=\;
\sum_i\phi(a_1,\dots,a_{r-2},e_i,e^i),
\]
where $\{e_i\}$, $\{e^i\}$ is a dual basis for the cyclic pairing.
This raises genus by~$1$ and lowers arity by~$2$: the shadow-level incarnation of the
BV operator $\Delta_{\mathrm{ns}}$.

\medskip

\noindent\textbf{Explicit Virasoro computation.}\enspace
On the Virasoro primary line, the conformal-weight-$2$ bar
cohomology is one-dimensional, spanned by the class~$x$ dual to the
stress tensor~$T$.  The Killing form is $H=\frac{c}{2}x^2$ and the
propagator is $P=\frac{2}{c}$.  The quartic contact invariant is
$Q^{\mathrm{contact}}_{\mathrm{Vir}}\cdot x^4$ with
$Q^{\mathrm{contact}}_{\mathrm{Vir}}=10/[c(5c+22)]$.  The genus loop
operator applied to this quartic:
\[
\Lambda_P\!\left(\frac{10}{c(5c+22)}\cdot x^4\right)
\;=\;
\binom{4}{2}\cdot\frac{2}{c}\cdot
\frac{10}{c(5c+22)}\cdot x^2
\;=\;
\frac{120}{c^2(5c+22)}\,x^2.
\]
Here $\binom{4}{2}=6$ counts leg selections and
$2/c$ is the propagator.  The result is the \emph{genus-one Hessian
correction} $\delta_{H,\mathrm{Vir}}^{(1)}=120/[c^2(5c+22)]\cdot x^2$.

The \emph{loop ratio}:
\[
\rho^{(1)}_{\mathrm{Vir}}
\;=\;
\frac{\Lambda_P(Q\cdot x^4)}{\kappa\cdot x^2}
\;=\;
\frac{120/[c^2(5c+22)]}{c/2}
\;=\;
\frac{240}{c^3(5c+22)}.
\]
This ratio is not determined by $\kappa=c/2$: it
detects the quartic structure of the Virasoro algebra through its
genus-one projection.  The asymptotic behaviour
$\rho^{(1)}\sim 48/c^4$ for $c\to\infty$ reflects the weakening of
quartic corrections in the semiclassical limit.

\subsection*{6.9.\enspace Quintic forcing and infinite towers}

The quintic obstruction determines whether the tower
terminates at arity~$4$.

\medskip

\noindent\textbf{Virasoro.}\enspace
The cubic shadow $\mathfrak C_{\mathrm{Vir}}$ and the quartic contact
invariant $Q^{\mathrm{contact}}_{\mathrm{Vir}}$ are both nonzero.
Their Poisson bracket under the Hodge pairing gives the quintic
obstruction:
\[
o^{(5)}_{\mathrm{Vir}}
\;=\;
\{\mathfrak C_{\mathrm{Vir}},\,
Q^{\mathrm{contact}}_{\mathrm{Vir}}\}_H
\;=\;
\frac{480}{c^2(5c+22)}\,x^5
\;\neq\;0.
\]
Since $o^{(5)}\neq 0$ for all $c\neq 0,-22/5$, the Virasoro shadow
tower does not terminate at any finite arity.  The tower is infinite:
$r_{\max}(\mathrm{Vir}_c)=\infty$.  The same holds for every
$\mathcal W_N$ algebra ($N\ge 2$): the cubic and quartic shadows
coexist and their bracket forces an infinite sequence of higher
obstructions.

\medskip

\noindent\textbf{Heisenberg.}\enspace
$\mathfrak C_{\cH}=0$ and $Q^{\mathrm{contact}}_{\cH}=0$.  The
quintic obstruction $o^{(5)}=\{0,0\}_H=0$.  Every higher obstruction
also vanishes.  The tower terminates at $r_{\max}=2$.

\medskip

\noindent\textbf{Affine.}\enspace
$\mathfrak C_{\widehat\fg}\neq 0$ but
$Q^{\mathrm{contact}}_{\widehat\fg}=0$ (the quaternary bracket
vanishes on bar cohomology by the PBW theorem for Kac--Moody
algebras).  The quintic obstruction
$o^{(5)}=\{\mathfrak C,0\}_H=0$.  The tower terminates at
$r_{\max}=3$.

\medskip

\noindent\textbf{$\beta\gamma$.}\enspace
$\mathfrak C_{\beta\gamma}=0$ (the Lie bracket is trivial on bar
cohomology) but $Q^{\mathrm{contact}}_{\beta\gamma}\neq 0$.
The quintic obstruction $o^{(5)}=\{0,Q\}_H=0$.  The tower terminates
at $r_{\max}=4$.

\medskip

\noindent
The pattern:
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lcccc}
& $\mathfrak C$ & $\mathfrak Q$
  & $o^{(5)}=\{\mathfrak C,\mathfrak Q\}_H$ & $r_{\max}$\\
\hline
Heisenberg & $0$ & $0$ & $0$ & $2$\\
Affine & $\neq 0$ & $0$ & $0$ & $3$\\
$\beta\gamma$ & $0$ & $\neq 0$ & $0$ & $4$\\
Virasoro & $\neq 0$ & $\neq 0$ & $\neq 0$ & $\infty$
\end{tabular}
\end{center}
Finite termination requires $\mathfrak C=0$ or
$\mathfrak Q=0$.  When both are nonzero, their bracket generates
the quintic, the quintic and quartic generate the sextic, and
the induction continues without bound: a transcendental potential
on the MC moduli.


\medskip

\noindent\textbf{The shadow growth rate.}\enspace
For class~M algebras (infinite shadow depth), the Taylor
coefficients $S_r$ of $\sqrt{Q_L}$ grow as
$S_r \sim A\cdot\rho(\cA)^r\cdot r^{-5/2}\cos(r\theta+\varphi)$,
where the \emph{shadow growth rate}
$\rho(\cA) = \sqrt{9\alpha^2+2\Delta}\,/\,(2|\kappa|)$
is a continuous invariant on the modular deformation space.
Self-dual Virasoro ($c=13$) has $\rho\approx 0.467$.
The critical cubic $5c^3+22c^2-180c-872=0$ has root
$c^*\approx 6.125$: the tower converges for $c>c^*$ and
diverges for $c<c^*$.

\medskip
\noindent\textbf{The shadow partition function.}\enspace
The double sum $Z^{\mathrm{sh}}_\cA =
\sum_{g,r} \hbar^{2g-2}\,Z_g^{(r)}$ converges absolutely.
Genus decay is at rate $1/(2\pi)^{2g}$
(Faber--Pandharipande $\lambda_g$-integral); arity decay is at
rate $\rho^r \cdot r^{-5/2}$ (Darboux analysis of the shadow
metric).  By contrast, the string partition function
diverges as $(2g{-}2)!$.  For Virasoro at $c=26$:
$\rho\approx 0.234$, and $Z^{\mathrm{sh}}$ has radius of
absolute convergence in both $\hbar$ and arity.

\subsection*{6.10.\enspace Independent sum factorisation}

For a direct sum $L=L_1\oplus L_2$ of Lie conformal algebras with
vanishing mixed OPE ($[L_1{}_\lambda L_2]=0$), all shadow invariants
separate:
\begin{align*}
\kappa(L_1\oplus L_2)
&=\kappa(L_1)+\kappa(L_2)
&&\text{(additive)},\\[3pt]
T^{\mathrm{br}}(L_1\oplus L_2)
&=T^{\mathrm{br}}(L_1)\oplus T^{\mathrm{br}}(L_2)
&&\text{(direct sum)},\\[3pt]
\Delta_{L_1\oplus L_2}(t)
&=\Delta_{L_1}(t)\cdot\Delta_{L_2}(t)
&&\text{(multiplicative)},\\[3pt]
R_4^{\mathrm{mod}}(L_1\oplus L_2)
&=R_4^{\mathrm{mod}}(L_1)+R_4^{\mathrm{mod}}(L_2)
&&\text{(additive)}.
\end{align*}
More generally, the full MC element factorises:
\[
\Theta_{L_1\oplus L_2}
\;=\;
\Theta_{L_1}\hat\otimes 1+1\hat\otimes\Theta_{L_2}
\;\in\;
\gAmod[L_1]\;\hat\otimes\;\gAmod[L_2],
\]
where $\hat\otimes$ is the completed tensor product with respect to
the depth filtration; at the level of partition functions,
$Z_{L_1\oplus L_2}=Z_{L_1}\cdot Z_{L_2}$.

The factorisation principle reduces computation for composite
algebras to their primitive summands.  Every algebra in the standard
landscape is either primitive (Heisenberg, Virasoro, $\beta\gamma$)
or built from primitive pieces by direct sum plus extension
(affine = current algebra over simple Lie, lattice = exponential
extension of Heisenberg, $\mathcal W_N$ = quantum Drinfeld--Sokolov
reduction of affine).  The full shadow obstruction tower of any composite
algebra is determined by its primitive constituents.
Drinfeld--Sokolov reduction is the \emph{shadow-depth escalator}
(Principle~\ref{princ:shadow-depth-escalator}): it sends
current-algebra systems (class~$\mathbf{L}$, $r_{\max}=3$,
finite towers) to $\mathcal{W}$-algebra systems
(class~$\mathbf{M}$, $r_{\max}=\infty$, infinite towers).
The nonlinearity of the Dirac bracket on the Slodowy slice creates
the quartic and all higher shadows; no finite truncation survives
the reduction.

\subsection*{6.11.\enspace The representation-theoretic perspective}

The categorical logarithm $\eta_{ij} = d\log(z_i - z_j)$ of
Section~1 is the integral kernel of a tautology: $D_\cA^2 = 0$ on
the modular bar complex.  From this identity, three structure theorems
emerge.  \emph{Algebraicity}: on each primary slice~$L$, the shadow
generating function satisfies $H(t)^2 = t^4 Q_L(t)$, where $Q_L$ is
a quadratic polynomial in three invariants $\kappa$, $\alpha$, $S_4$
(Theorem~\ref{thm:riccati-algebraicity}).  \emph{Formality}: the
genus-$0$ shadow obstruction tower is the $L_\infty$ formality obstruction tower
(Theorem~\ref{thm:shadow-formality-identification}); the four depth
classes G/L/C/M are the corresponding formality types, while
positive-genus corrections form a separate quantum layer.
\emph{Complementarity}: for a Koszul pair $(\cA, \cA^!)$, the summands
$\mathbf Q_g(\cA) \oplus \mathbf Q_g(\cA^!)$ are Lagrangian
(Theorem~C).

The discriminant $\Delta = 8\kappa S_4$ governs the
single-line dichotomy: on each primary deformation line,
$\Delta = 0$ forces tower termination ($L_\infty$-formality)
and $\Delta \neq 0$ forces an infinite tower
(intrinsic non-formality).  The contact class~C ($r_{\max} = 4$,
$\beta\gamma$) escapes via stratum separation.  No classical invariant of an algebra over a point
sees $\Delta$: it is visible only on curves of positive genus, where
the Arnold relation acquires a defect.

Classical Koszul duality (Priddy, Beilinson--Ginzburg--Soergel)
occupies genus~$0$, arity~$2$, $\Delta = 0$: the formal, class-G
case.  The $R$-matrix of quantum groups arises as the genus-$0$
shadow
$\mathrm{Sh}_{0,2}(\Theta_{\widehat{\fg}_k})$ (\S7.7).
At the critical level $k = -h^\vee$, the scalar class vanishes
($\kappa = 0$) and bar cohomology recovers the Feigin--Frenkel
center $\operatorname{Fun}(\mathrm{Op}_{{}^L\fg})$; the Langlands
programme lives on this orthogonal axis, not in the MC element
but in the cohomology that emerges on the uncurved scalar locus.

% ====================================================================
\section*{7.\quad The standard landscape}
% ====================================================================

The machine of Sections~1--6 accepts any chiral algebra as input.
The seven families
below exhaust the standard Lie-theoretic landscape: each exhibits a
different bar-complex structure, shadow archetype,
genus-two shell profile, and completion
behaviour.  No two families share all four invariants; taken
together, they realise every depth class (G/L/C/M), every curvature
sign, and every pattern of genus-two shell activation.

For each family we display the complete OPE,
bar complex with explicit differential, Koszul dual,
shadow obstruction tower with depth classification, modular characteristic
with complementarity, genus-two shell profile, and any structural
feature unique to that family.


% ----- 7.1 Heisenberg -----
\subsection*{7.1.\quad Heisenberg}

The Gaussian archetype: shadow depth~$2$,
the tower terminates at arity~$2$, and every higher-genus invariant is
determined by~$\kappa$ alone.

A single bosonic field $\alpha$ of conformal weight~$1$.  The OPE is
\[
\alpha(z)\,\alpha(w)
\;\sim\;
\frac{k}{(z-w)^2}.
\]
No simple pole: the singularity is purely of order~$2$.  The mode
algebra is the Heisenberg Lie algebra
$[\alpha_m,\alpha_n]=km\,\delta_{m+n,0}$, and the vertex algebra
$\mathcal H_k$ is the vacuum module at level~$k\neq 0$.  Central
charge $c=1$.

\medskip
\noindent\textbf{Bar complex.}
The augmentation ideal
$\bar{\mathcal H}_k=\mathcal H_k/\mathbb C\cdot\mathbf{1}$ is
spanned by normally ordered monomials in~$\alpha$ and its
derivatives.  The bar construction is the tensor coalgebra on the
desuspension:
\[
\barB(\mathcal H_k)
\;=\;
T^c\!\bigl(s^{-1}\bar{\mathcal H}_k\bigr),
\qquad
d_{\barB}\bigl(s^{-1}a_1|\cdots|s^{-1}a_n\bigr)
\;=\;
\sum_{i<j}\pm\,
s^{-1}a_1|\cdots|s^{-1}\operatorname{Res}_{z_i=z_j}
\bigl(a_i(z_i)\,a_j(z_j)\,\eta_{ij}\bigr)|\cdots|s^{-1}a_n.
\]
Because the only singularity is a double pole (producing a scalar),
$d_{\barB}$ acts by contraction: it pairs two tensor factors and
replaces them by a scalar.  Explicitly:
\begin{align*}
d_{\barB}(s^{-1}\alpha) &= 0,\\
d_{\barB}(s^{-1}\alpha|s^{-1}\alpha) &=
  k\cdot s^{-1}\mathbf{1} = 0 \quad
  \text{(in the reduced complex)},\\
d_{\barB}(s^{-1}\partial^m\alpha|s^{-1}\partial^n\alpha) &=
  k\binom{m+n+1}{m}\cdot s^{-1}\mathbf{1} = 0 \quad (m+n\ge 1).
\end{align*}
Bar cohomology concentrates:
\[
H^1\bigl(\barB(\mathcal H_k)\bigr) = \mathbb C\cdot\alpha^*,
\qquad
H^n\bigl(\barB(\mathcal H_k)\bigr) = 0 \;\;\text{for}\;\; n\ge 2.
\]
PBW concentration: bar cohomology is one-dimensional in degree~$1$.

\medskip
\noindent\textbf{Koszul dual.}
The bar cohomology $\cA^{\mathrm i}=H^*(\barB(\mathcal H_k))$
is a one-dimensional graded coalgebra concentrated in degree~$1$.
Taking graded linear duals gives the Koszul dual algebra:
\[
\mathcal H_k^!
\;:=\;
\bigl(\cA^{\mathrm i}\bigr)^\vee
\;=\;
\bigl(\operatorname{Sym}^{\mathrm{ch}}(V^*),\;m_0=-k\omega\bigr),
\]
where $V^*=\mathbb C\cdot\alpha^*$ is the dual generator space and
$m_0=-k\omega$ is the curvature: a curving element, not a
differential.  The curved $A_\infty$-relation reads
$m_1^2(a)=[m_0,a]$ (commutator, with sign).  The Koszul dual of
Heisenberg is \emph{not} Heisenberg: $\mathcal H_k^!$ is a
\emph{curved} symmetric algebra, while $\mathcal H_k$ is a
\emph{flat} vertex algebra.  Chiral
Koszul duality is not an involution but a Verdier-type reflection.

\medskip
\noindent\textbf{Shadow obstruction tower.}
The OPE has no simple pole: $\alpha_{(0)}\alpha=0$.
Every transferred operation beyond arity~$2$ vanishes,
so the only stable graphs contributing
to~\eqref{eq:pref-theta} have all vertices of valence~$2$;
stability forces $g(v)\ge 1$ at each bivalent vertex.
Since the only nonvanishing OPE coefficient is the scalar~$k$
and the desuspended generator $s^{-1}\eta$ has odd degree,
the parity argument
(Theorem~\ref{thm:mc2-bar-intrinsic})
forces the graph sum to collapse:
\[
\Theta_{\mathcal H_k}
\;=\;
k\cdot\eta\otimes\Lambda,
\]
where $\eta=d\log(z_1-z_2)$ is the propagator on
$\operatorname{FM}_2(X)$ and
$\Lambda=\lambda_1\in H^2(\overline{\cM}_{1,1})$ is the
generator of $H^*(\overline{\cM}_{1,1})$.
The five-component differential collapses completely:
\begin{itemize}[nosep]
\item $d_{\mathrm{Ch}_\infty}=0$: no higher transferred operations,
\item $d_{\mathrm{coll}}=0$: collisions produce scalars only,
\item $d_{\mathrm{pf}}=0$: no planted-forest contributions,
\item only $d_{\check C}+d_{\mathrm{loop}}$ survive.
\end{itemize}
Cubic shadow: $\mathfrak{C}(\mathcal H_k)=0$.  Quartic contact
shadow: $Q^{\mathrm{contact}}(\mathcal H_k)=0$.  All higher
obstructions vanish.  Shadow depth~$2$.  Gaussian archetype.

\medskip
\noindent\textbf{Modular characteristic and complementarity.}
\[
\kappa(\mathcal H_k) = k,
\qquad
\kappa(\mathcal H_k^!) = -k,
\qquad
\kappa(\mathcal H_k)+\kappa(\mathcal H_k^!) = 0.
\]
A single scalar $\kappa(\cH_k)=k$ determines every
projection: the generating function is
$\sum_{g\ge 1}F_g\,x^{2g}=k\bigl(\frac{x/2}{\sin(x/2)}-1\bigr)
= k\bigl(\hat A(ix)-1\bigr)$,
giving $F_1=k/24$, $F_2=7k/5760$, $F_3=31k/967680$, \ldots
(the Taylor coefficients of the $\hat{A}$-genus).
At genus~$g$, $Q_g(\mathcal H_k)$ is a polynomial of degree~$2g$
in~$k$, computed entirely from iterated loop contractions of the
single propagator~$\eta$.

\medskip
\noindent\textbf{Genus-two shell profile.}
Only the loop$\circ$loop shell contributes:
\[
\Theta^{(2)}_{\mathrm{loop}\circ\mathrm{loop}}\neq 0,
\qquad
\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}= 0,
\qquad
\Theta^{(2)}_{\mathrm{pf}}= 0.
\]
Every genus correction reduces to iterated loop contractions of a
single propagator: the Gaussian measure of chiral algebra theory.

% ----- 7.2 Kac-Moody -----
\subsection*{7.2.\quad Affine Kac--Moody}

The Lie/tree archetype: shadow
depth~$3$, the cubic shadow is the Lie bracket, and the Jacobi
identity kills all higher obstructions.  The first family
with a nonabelian bar differential.

Let $\mathfrak g$ be a simple Lie algebra of rank~$\ell$,
dimension~$d=\dim\mathfrak g$, dual Coxeter number~$h^\vee$,
with structure constants $f^{ab}{}_c$ and normalised Killing
form~$\kappa^{ab}$.  The affine vertex algebra
$\widehat{\mathfrak g}_k$ has generators $J^a$,
$a=1,\dots,d$, of conformal weight~$1$, with OPE
\[
J^a(z)\,J^b(w)
\;\sim\;
\frac{f^{ab}{}_c\,J^c(w)}{z-w}
\;+\;
\frac{k\,\kappa^{ab}}{(z-w)^2}.
\]
Both pole orders are present.  The simple pole carries the Lie
bracket; the double pole carries the invariant inner product at
level~$k$.  The mode algebra is the affine Lie algebra
$\widehat{\mathfrak g}$:
\[
[J^a_m,J^b_n]
\;=\;
f^{ab}{}_c\,J^c_{m+n}
\;+\;
km\,\kappa^{ab}\,\delta_{m+n,0}.
\]

\medskip
\noindent\textbf{Bar complex.}
The simple-pole residue contributes a bracket component
to~$d_{\barB}$:
\[
d_{\barB}(s^{-1}J^a|s^{-1}J^b)
\;=\;
f^{ab}{}_c\,s^{-1}J^c
\;+\;
k\,\kappa^{ab}\cdot(\text{curvature term}).
\]
The bracket component is the Chevalley--Eilenberg differential of
$L\mathfrak g$; the curvature component is the central
extension by~$k$.  The identity $d_{\barB}^2=0$ requires the
\emph{Borcherds identity}, not Jacobi: the $n$-fold residue relations from all pole orders
simultaneously, replacing $[d,[d,-]]=0$.

\medskip
\noindent\textbf{PBW spectral sequence.}
Filter $\barB(\widehat{\mathfrak g}_k)$ by conformal weight.  The
spectral sequence $E_1^{p,q}(g)$ at genus~$g$ has $E_1$ page given
by the bar cohomology of the associated graded, a free-field
computation in the Heisenberg algebra
$\mathcal H_k^{\otimes d}$.  PBW concentration at all genera is
proved: $E_\infty^{p,q}(g)=0$ for $q\neq 0$.  The enriched
genus-$g$ $E_1$ page carries the structure of a free resolution of the
diagonal $\widehat{\mathfrak g}_k$-bimodule, with the Hodge
bundle~$\mathbb E$ supplying the curvature twist at each genus.

\medskip
\noindent\textbf{Sugawara construction.}
At non-critical level $k\neq -h^\vee$, the stress tensor is
\[
T(z)
\;=\;
\frac{1}{2(k+h^\vee)}
\sum_{a=1}^{d}{:}J^a(z)J^a(z){:}\,,
\qquad
c
\;=\;
\frac{k\,\dim\mathfrak g}{k+h^\vee}.
\]
The Sugawara field is composite, not in the generating set.  At
$k=-h^\vee$, the construction is
\emph{undefined} ($c$ does not exist, not ``$c$ diverges'').  The Feigin--Frenkel
center $\mathfrak z(\widehat{\mathfrak g}_{-h^\vee})\cong
\operatorname{Fun}(\operatorname{Op}_{{}^L\fg}(D))$
is a commutative vertex algebra of ${}^L\mathfrak g$-opers on the formal disk.  At critical level, the bar
complex is flat but noncommutative.

\medskip
\noindent\textbf{Shadow obstruction tower.}
The cubic shadow is the Lie bracket itself:
\[
\mathfrak C(\widehat{\mathfrak g}_k)
\;=\;
\bigl[f_{abc}\,J^a\otimes J^b\otimes J^c\bigr]
\;\in\;
H^1(F^3\mathfrak g^{\mathrm{mod}}/F^4\mathfrak g^{\mathrm{mod}},\,d_2).
\]
The quartic obstruction $o^{(4)}(\widehat{\mathfrak g}_k)=0$: the
Jacobi identity on~$\mathfrak g$ kills the only candidate quartic
cocycle via $f^{ab}{}_e f^{ec}{}_d+\text{cyclic}=0$.  The quintic
obstruction vanishes by the same mechanism.  Shadow depth~$3$.
Lie/tree archetype.

\medskip
\noindent\textbf{Modular characteristic and complementarity.}
\[
\kappa(\widehat{\mathfrak g}_k)
\;=\;
\frac{(k+h^\vee)\dim\mathfrak g}{2h^\vee},
\qquad
\kappa(\widehat{\mathfrak g}_k^!)
\;=\;
-\frac{(k+h^\vee)\dim\mathfrak g}{2h^\vee}.
\]
Complementarity: $\kappa(\widehat{\mathfrak g}_k)+
\kappa(\widehat{\mathfrak g}_k^!)=0$ for all $k\neq -h^\vee$.
The Feigin--Frenkel involution
\[
k\;\longleftrightarrow\; -k-2h^\vee
\]
is Koszul duality in the modular sense: the level of the dual algebra
is the Langlands dual level.  The complementarity sum $c(k)+c(-k-2h^\vee)=2\dim\mathfrak g$
becomes the complementarity relation evaluated on this family.

\medskip
\noindent\textbf{Genus-two shell profile.}
At genus~$2$, the loop$\circ$loop and sep$\circ$loop shells both
contribute:
\[
\Theta^{(2)}_{\mathrm{loop}\circ\mathrm{loop}}\neq 0,
\qquad
\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}\neq 0,
\qquad
\Theta^{(2)}_{\mathrm{pf}}= 0.
\]
The planted-forest shell vanishes because the quartic shadow is zero
and planted forests require arity~$\ge 4$.  Separating degeneration
activates through the cubic shadow (the Lie bracket) composed with
the loop contraction: the genus-two correction factors through
$\mathfrak g \otimes \mathfrak g \xrightarrow{[-,-]}
\mathfrak g \xrightarrow{\mathrm{loop}} \mathbb C$.

\medskip
\noindent\textbf{Special feature: Feigin--Frenkel at critical level.}
At $k=-h^\vee$, the vertex algebra
$\widehat{\mathfrak g}_{-h^\vee}$ has a large center.
The center $\mathfrak z(\widehat{\mathfrak g}_{-h^\vee})
\cong \operatorname{Fun}(\operatorname{Op}_{{}^L\mathfrak g}(D))$
is the ring of opers on the formal disk for the Langlands dual.  The
bar complex at critical level is \emph{flat} ($m_0^{(1)}=0$): the
modular characteristic $\kappa(-h^\vee)=0$.  Critical-level chiral
Koszul duality is the geometric Langlands correspondence at the
level of the bar construction.


% ----- 7.3 Virasoro -----
\subsection*{7.3.\quad Virasoro}

The mixed archetype: shadow depth infinity,
the tower never terminates, and new invariants appear at every arity.
The self-coupling $T_{(1)}T = 2T$ drives all nonlinear
complexity.

One generator~$T$ of conformal weight~$2$.  The OPE is
\[
T(z)\,T(w)
\;\sim\;
\frac{c/2}{(z-w)^4}
\;+\;
\frac{2\,T(w)}{(z-w)^2}
\;+\;
\frac{\partial T(w)}{z-w}.
\]
Three pole orders: the fourth-order pole carries~$c$;
the second-order pole carries $T_{(1)}T=2T$; the simple pole
carries~$\partial T$.  The mode algebra:
\[
[L_m,L_n]
\;=\;
(m-n)L_{m+n}
\;+\;
\frac{c}{12}(m^3-m)\,\delta_{m+n,0}.
\]

\medskip
\noindent\textbf{Bar complex.}
The bar differential on the Virasoro vacuum module has three components:
\begin{align*}
d_{\barB}(s^{-1}T|s^{-1}T)
&=
2\,s^{-1}T + \frac{c}{2}\cdot(\text{curvature})
\quad\text{(from $(z-w)^{-2}$ and $(z-w)^{-4}$ poles)},\\
d_{\barB}(s^{-1}T|s^{-1}\partial T)
&=
s^{-1}\partial T + 3\,s^{-1}T
\quad\text{(from $(z-w)^{-1}$ and $(z-w)^{-2}$ poles)}.
\end{align*}
At higher tensor degree, the bar differential on
$s^{-1}T|s^{-1}T|s^{-1}T$ produces terms involving the
self-coupling $T_{(1)}T=2T$ composed with itself, the first
instance of a bar differential that is genuinely quadratic in the
structure constants.  PBW concentration still holds: at every
genus~$g$, the spectral sequence collapses to $E_\infty^{p,0}$.

\medskip
\noindent\textbf{Koszul dual.}
\[
\operatorname{Vir}_c^!
\;=\;
\operatorname{Vir}_{26-c}.
\]
The duality is an involution on the one-parameter Virasoro family.
The fixed point is $c=13$, \emph{not}~$c=26$.  Self-duality:
$\operatorname{Vir}_c \cong \operatorname{Vir}_c^!$ iff $c=13$.
The central charge~$26$ plays no special role in Koszul duality; its
appearance in string theory is the vanishing of
$\kappa(\operatorname{Vir}_{26})=13$,
$\kappa(\operatorname{Vir}_{26}^!)=\kappa(\operatorname{Vir}_0)=0$: the
\emph{anomaly-cancellation} condition, not the self-duality condition.

The same-family shadow $\operatorname{Vir}_{26-c}$ is the
depth-zero resonance shadow: the image of the finite-dimensional
resonance truncation $R_{\mathrm{Vir}}$, not the final Koszul dual in
the completed sense.  The genuine $\mathcal W_\infty$-type dual
requires the full resonance-filtered completion.

\medskip
\noindent\textbf{Shadow obstruction tower.}
The cubic shadow is determined by the self-coupling $T_{(1)}T=2T$:
\[
\mathfrak{C}_{\mathrm{Vir}} \;\neq\; 0.
\]
The quartic contact shadow, extracted from the four-point collision
residue on $\overline{C}_4(\mathbb P^1)$, is
\[
Q^{\mathrm{contact}}_{\mathrm{Vir}}
\;=\;
\frac{10}{c(5c+22)}.
\]
The poles at $c=0$ and $c=-22/5$ reflect the degeneration of the
Virasoro vacuum module: at $c=0$ the identity representation
degenerates, and at $c=-22/5$ the $(2,5)$ minimal model forces the
vacuum Verma module to acquire a singular vector at weight~$4$.

The quintic obstruction is the Poisson bracket in the shadow algebra:
\[
o^{(5)}_{\mathrm{Vir}}
\;=\;
\bigl\{C_{\mathrm{Vir}},\,
Q^{\mathrm{contact}}_{\mathrm{Vir}}\bigr\}_H
\;=\;
\frac{480}{c^2(5c+22)}\,x^5
\;\neq\; 0.
\]
Since $o^{(5)}\neq 0$, no finite truncation captures the
Virasoro algebra.  Shadow depth~$\infty$.  Mixed archetype.

\medskip
\noindent\textbf{Modular characteristic and complementarity.}
\[
\kappa(\operatorname{Vir}_c) = \frac{c}{2},
\qquad
\kappa(\operatorname{Vir}_{26-c}) = \frac{26-c}{2} = 13 - \frac{c}{2},
\qquad
\kappa(\operatorname{Vir}_c)+\kappa(\operatorname{Vir}_c^!)
= 13.
\]
This is the unique standard family where complementarity gives a
\emph{nonzero} constant: $\kappa+\kappa^!=13$ rather than~$0$.  The
constant~$13$ is half the critical dimension~$26$, and its
nonvanishing reflects that $\operatorname{Vir}$ is a
one-generator algebra whose bar complex has nontrivial
self-coupling: the curvature of the dual cannot cancel the curvature
of the algebra when both live in the same one-dimensional family.

\medskip
\noindent\textbf{Higher-genus corrections.}
At genus~$1$, the shadow obstruction tower produces corrections beyond the
linear curvature.  The genus-$1$ Hessian correction:
\[
\delta H^{(1)}_{\mathrm{Vir}}
\;=\;
\frac{120}{c^2(5c+22)}\cdot x^2.
\]
The loop ratio:
\[
\rho^{(1)}_{\mathrm{Vir}}
\;=\;
\frac{240}{c^3(5c+22)}.
\]
The Hessian correction $\delta H^{(1)}$ is the genus-$1$ quadratic
deviation from the linearised curvature; the loop
ratio~$\rho^{(1)}$ is the ratio of the quadratic correction
to~$\kappa^2$.  Both are determined by the quartic contact shadow
and are not determined by~$\kappa=c/2$: they are the
first nonlinear genus-$1$ invariants, visible only because the shadow
tower has depth~$\ge 4$.

\medskip
\noindent\textbf{Genus-two shell profile.}
All three primitive shells contribute:
\[
\Theta^{(2)}_{\mathrm{loop}\circ\mathrm{loop}}\neq 0,
\qquad
\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}\neq 0,
\qquad
\Theta^{(2)}_{\mathrm{pf}}\neq 0.
\]
The loop$\circ$loop shell comes from iterated curvature; the
sep$\circ$loop shell from mixed clutching; and the planted-forest
shell from the quartic contact channel~$Q^{\mathrm{contact}}$.  The
Virasoro algebra is the simplest family in which the planted-forest
shell is nonzero, the first family that sees the log-FM boundary
strata of $\overline{\mathcal M}_{2,n}$.



\medskip

\noindent\textbf{The critical dimension.}\enspace
\[
\nabla^{\mathrm{hol}}_c
\;=\;
d
\;-\;\frac{c}{2}\,\omega_g
\;-\;\frac{10}{c(5c+22)}\,\delta_4
\;-\;\frac{120}{c^2(5c+22)}\,\delta_H
\;-\;\cdots\,.
\]
The connection is flat for every~$c$ by the MC equation.
The critical dimension $c=26$ arises from the \emph{dual}
curvature vanishing:
\[
\kappa(\mathrm{Vir}_{26-c})\;=\;\frac{26-c}{2}\;=\;0
\qquad\Longrightarrow\qquad
\boxed{\;c\;=\;26\;}.
\]
At $c=26$ the Koszul dual
$\mathrm{Vir}_{26}^!=\mathrm{Vir}_0$ is \emph{uncurved}:
the dual bar complex is a genuine cochain complex.
The quartic contact correction evaluates to
$\mathfrak Q^{\mathrm{contact}}_{26}
=10/(26\cdot 152)=5/1976$.
The algebra itself retains curvature $\kappa=13$; it is
the depth-zero resonance shadow $\mathrm{Vir}_{26-c}$
at $c=26$ that is trivial.
The holographic datum $\mathcal H(\mathrm{Vir}_{26})$
has unobstructed dual; this is the string-theoretic content
of the critical dimension.

The Polyakov formula (\cite{Pol87}) for a single scalar on a
surface~$\Sigma$ with conformal factor~$\sigma$ ($g_1=e^{2\sigma}g_0$) is
\[
\log\frac{\det'\!\Delta_{g_1}}{\det'\!\Delta_{g_0}}
\;=\;
-\frac{1}{6\pi}\int_\Sigma
\bigl(|\nabla\sigma|^2+R_{g_0}\,\sigma\bigr)\,d\mu_{g_0}.
\]
This is the arity-$2$ shadow evaluation at $\kappa=1$: for
general~$\kappa$, on the proved uniform-weight scalar lane (Definition~\ref{def:scalar-lane}) the
minimal shadow satisfies
$\Theta^{\min}_\cA=\kappa\cdot\eta\otimes\Lambda$
evaluates against~$\sigma$ to give
$\langle\Theta^{\min},\sigma\rangle
=-(\kappa/6\pi)\int(|\nabla\sigma|^2+R\sigma)\,d\mu$,
reproducing the conformal anomaly with coefficient~$\kappa/(6\pi)$.
The higher-arity corrections $\delta_4,\delta_H,\ldots$ displayed
in the shadow connection above are inaccessible to the free-field
path integral: they require the shadow obstruction tower.
For uniform-weight algebras, the genus expansion is controlled
by the $\hat{A}$-genus:
\begin{equation}\label{eq:ahat-universality-preface}
\textstyle
F_g(\cA) \;=\; \kappa(\cA)\cdot\lambda_g^{\mathrm{FP}},
\qquad
\sum_{g\geq 1} F_g\,x^{2g}
\;=\;
\kappa\bigl(\hat{A}(ix) - 1\bigr)
\;=\;
\kappa\Bigl(\frac{x/2}{\sin(x/2)} - 1\Bigr).
\end{equation}
The Taylor coefficients $\lambda_g^{\mathrm{FP}}$ are the
Faber--Pandharipande evaluations of the Hodge class: $\lambda_1^{\mathrm{FP}} = 1/24$,
$\lambda_2^{\mathrm{FP}} = 7/5760$,
$\lambda_3^{\mathrm{FP}} = 31/967680$
(Theorem~\ref{thm:universal-generating-function}).
The series converges:
$|F_g|\sim 2|\kappa|/(2\pi)^{2g}$
(exponential decay), in contrast to the bosonic string where
$F_g\sim(2g{-}2)!$ from the noncompactness of~$\mathbf{R}^d$.
The critical dimension is the zero of the dual curvature
$\kappa(\mathrm{Vir}_{26-c})=(26-c)/2$.

% ----- 7.4 W_3 -----
\subsection*{7.4.\quad $\boldsymbol{\mathcal W_3}$}

The first multi-generator family:
two generators of different conformal weights produce cross-channel
mixing in the genus-$1$ Hessian, a $2\times 2$ spectral
discriminant, and the first multi-channel genus-$2$
amplitude.  Infinite shadow depth, with
propagator mixing as a new structural feature.

Two generators: the stress tensor~$T$ (weight~$2$) and a primary
field~$W$ (weight~$3$).  The $TT$~OPE is Virasoro.  The $TW$~OPE
encodes the primary property:
\[
T(z)\,W(w)
\;\sim\;
\frac{3\,W(w)}{(z-w)^2}
\;+\;
\frac{\partial W(w)}{z-w}.
\]
The $WW$~OPE is the first genuinely nonlinear datum in the standard
landscape:
\begin{align*}
W(z)\,W(w)
\;\sim\;\;
&\frac{c/3}{(z-w)^6}
\;+\;
\frac{2\,T(w)}{(z-w)^4}
\;+\;
\frac{\partial T(w)}{(z-w)^3}\\[4pt]
&+\;
\frac{1}{(z-w)^2}
\biggl[
\frac{16}{22+5c}\,\Lambda(w)
\;+\;
\frac{3}{10}\,\partial^2 T(w)
\biggr]
\;+\;\cdots\,,
\end{align*}
where the composite field
\[
\Lambda
\;=\;
{:}TT{:}\;-\;\tfrac{3}{10}\,\partial^2 T
\]
is the unique quasi-primary of weight~$4$ in the vacuum module.  The
coefficient $-3/10$ is fixed by requiring $T(z)\Lambda(w)$ to have
no third-order pole: quasi-primary projection orthogonal to the
descendant~$\partial^2 T$.  The structure constant
$16/(22+5c)$ governs the $WW\Lambda$ coupling.

\medskip
\noindent\textbf{The $c=-22/5$ degeneration.}
At $c=-22/5$, the denominator vanishes and $\Lambda$ becomes a null
field.  The vacuum Verma module has a singular vector at weight~$4$:
the Kac determinant vanishes there, and $\mathcal W_3$ is not
finitely generated by $T$ and~$W$ alone.  Infinitely many new
generators are required.  This is the first $\mathcal W$-algebra
where the structure constants have poles in the central charge.

\medskip
\noindent\textbf{Shadow obstruction tower.}
The cubic shadow inherits the Virasoro self-coupling $T_{(1)}T=2T$
and acquires a contribution from $T_{(1)}W=3W$:
$\mathfrak{C}_{\mathcal W_3}\neq 0$.  The quartic contact channel
is the composition
\[
W\otimes W
\;\xrightarrow{\text{OPE at }(z-w)^{-2}}\;
\Lambda
\;\xrightarrow{\text{OPE of }{:}TT{:}}\;
T\otimes T,
\]
which factors through the quasi-primary projection and then the
Virasoro OPE.  This factorisation is represented in the bar complex
by a planted forest with two leaves and an internal vertex of
weight~$4$: the first time a planted-forest correction appears in the
bar differential.

The quartic contact shadow includes the Virasoro contribution
$Q^{\mathrm{contact}}_{\mathrm{Vir}}=10/[c(5c+22)]$ plus an
additional term from the $WW\Lambda$ channel, proportional to
$16/(22+5c)$.  Both are singular at $c=-22/5$: the quartic shadow
detects the vacuum degeneracy.  Shadow depth~$\infty$.  Mixed modular
archetype.

\medskip
\noindent\textbf{Modular characteristic.}
\[
\kappa(\mathcal W_3)
\;=\;
\frac{5c}{6}\,.
\]
The weight-$2$ generator contributes $c/2$ and the weight-$3$
generator contributes $c/3$, giving
$\kappa=c/2+c/3=5c/6$.  The Koszul dual
$\mathcal W_3^!$ is a $\mathcal W_3$-algebra at the dual central
charge $c'=100-c$ (self-dual at $c=50$); complementarity:
$\kappa(\mathcal W_3{}_c)+\kappa(\mathcal W_3{}_{100-c})=250/3$.

\medskip
\noindent\textbf{Genus-two shell profile.}
All three shells are active:
$\Theta^{(2)}_{\mathrm{loop}\circ\mathrm{loop}}\neq 0$,
$\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}\neq 0$,
$\Theta^{(2)}_{\mathrm{pf}}\neq 0$.
The planted-forest shell is sensitive to the $WW\Lambda$ channel:
$\mathcal W_3$ is the first family that is genuinely planted-forest
sensitive, detecting log-FM boundary strata that are invisible to
Heisenberg and affine Kac--Moody.
The genus-$2$ free energy decomposes as
\begin{equation}\label{eq:w3-genus2-preface}
F_2(\cW_3)
= \underbrace{\frac{7c}{6912}}_{\kappa \cdot \lambda_2^{\mathrm{FP}}}
\;+\;
\underbrace{\frac{c+120}{16c}}_{\delta F_2},
\end{equation}
where $\delta F_2 = (c{+}120)/(16c)$ is the cross-channel
correction from mixed $TW$-propagator graphs, verified by
graph-by-graph recomputation over all seven genus-$2$ stable graphs
(Remark~\ref{rem:w3-genus2-cross-channel}).  This is the first
explicit multi-channel genus-$2$ amplitude;  the scalar part
$\kappa\cdot\lambda_2^{\mathrm{FP}}$ is unconditional, the
cross-channel correction is conditional on
Open Problem~\ref{op:multi-generator-universality}.



\medskip

\noindent\textbf{The $\mathcal W_3$ holographic datum.}\enspace
The deformation space of the modular MC problem is two-dimensional:
deformations along $\partial_c T$ and along $\partial_c W$.
At $c=0$: $\kappa=0$ and the bar complex is uncurved.
The dual curvature vanishes at $c=100$ ($K=c+c'=100$).
The Hessian eigenvalue $\kappa_c=(c-50)/2$ (defined below) governs
the spectral discriminant; its zero at $c=50$ (the FF fixed point)
is the $\mathcal W_3$ self-dual central charge.

The quartic contact shadow is controlled by the quasi-primary
\[
\Lambda\;=\;{:}TT{:}-\tfrac{3}{10}\,\partial^2 T,
\qquad
[\ell_4^{(0)}]
\;=\;
\frac{16}{22+5c}\;\Lambda.
\]
At $c=-22/5$ (the $(2,5)$ minimal model) the quartic diverges;
this is a resonance point of the $\mathcal W_3$ shadow obstruction tower,
shared with Virasoro.

The genus-$1$ tangent map is a $2\times 2$ matrix
\[
H^{(1)}_{\mathcal W_3}
\;=\;
\begin{pmatrix}
\kappa_c & 0 \\[2pt]
0 & \kappa_c + \dfrac{48}{5c+22}
\end{pmatrix},
\qquad
\kappa_c \;:=\; \frac{c-50}{2}\,,
\]
in the basis $(\partial_c T,\,\partial_c W)$; here $\kappa_c$
is the Hessian eigenvalue, \emph{not} the modular
characteristic $\kappa=5c/6$.  Its determinant
is the spectral discriminant
\[
\Delta_{\mathcal W_3}(x)
\;=\;
\bigl(1-\kappa_c\,x\bigr)
\Bigl(1-\Bigl(\kappa_c+\frac{48}{5c+22}\Bigr)x\Bigr).
\]
The two branch points $x_1=1/\kappa_c$ and
$x_2=(5c+22)/(\kappa_c(5c+22)+48)$ are the reciprocals of the
eigenvalues of the genus-$1$ Hessian.
They coincide at the resonance value
$c=-22/5+48/(5\kappa_c)$, where the two deformation
directions merge.

The holographic datum:
\[
\mathcal H(\mathcal W_3{}_c)
\;=\;
\Bigl(
\mathcal W_3{}_c,\;
\mathcal W_3{}_{100-c},\;
\cC_c^{W_3},\;
r_c^{W_3}(z),\;
\Theta_c,\;
\nabla^{\mathrm{hol}}_c
\Bigr),
\]
with Koszul dual $\mathcal W_3{}_{100-c}$
($\kappa_c+\kappa_{100-c}=250/3$, self-dual at $c = 50$), line-operator category
$\cC_c^{W_3}$ a module category for the dg-shifted $W_3$-Yangian,
and shadow connection
\[
\nabla^{\mathrm{hol}}_c
\;=\;
d
\;-\;\frac{5c}{6}\,\omega_g
\;-\;\frac{16}{22+5c}\,\Lambda\cdot\delta_4
\;-\;\cdots\,.
\]

% ----- 7.5 beta-gamma -----
\subsection*{7.5.\quad $\boldsymbol{\beta\gamma}$ system}

The $\beta\gamma$ system is the contact archetype: the first
nonlinearity appears at arity~$4$ (not~$3$), and a rank-one abelian
rigidity argument kills it, producing shadow depth~$4$.  This is the
unique standard family in which the tower terminates for a structural
reason distinct from Lie-algebraic cancellation.

Two fields: $\beta$ of conformal weight~$\lambda$ and $\gamma$ of
conformal weight~$1-\lambda$.  The OPE is
\[
\beta(z)\,\gamma(w)
\;\sim\;
\frac{1}{z-w},
\qquad
\beta(z)\,\beta(w)\;\sim\;0,
\qquad
\gamma(z)\,\gamma(w)\;\sim\;0.
\]
A simple pole with no double pole: the contact archetype.  Central
charge $c_{\beta\gamma}=3(2\lambda-1)^2-1=12\lambda^2-12\lambda+2$.
At the standard weight $\lambda=1$, $c_{\beta\gamma}=2$
(the fermionic $bc$~ghost system has $c_{bc}=-2$).

\medskip
\noindent\textbf{Shadow obstruction tower.}
The cubic shadow on the weight line vanishes: $\ell_3^{(0)}=0$,
because $\beta$ and $\gamma$ carry different conformal weights and the
three-point residue on the diagonal weight sector is zero.  The
quartic operation is nonzero: $\ell_4^{(0)}\neq 0$, from the
four-point function
$\langle\beta\gamma\beta\gamma\rangle$.  This is the defining
property of the contact archetype: the first nonlinearity appears at
arity~$4$, not~$3$.

The quartic contact invariant
$\mu_{\beta\gamma}=\langle\eta,m_3(\eta,\eta,\eta)\rangle=0$ vanishes
by rank-one abelian rigidity: the $\beta\gamma$~system has a
$\mathrm{U}(1)$ ghost-number symmetry, and the cyclic pairing
on the deformation complex vanishes on the arity-$4$ component by
weight considerations.  The quintic obstruction vanishes because the
cubic shadow is zero: $o^{(5)}=\{0,Q\}_H=0$.  Shadow depth~$4$.
Contact/quartic archetype.

\medskip
\noindent\textbf{Koszul dual.}
The Koszul dual is the $bc$~ghost system: $(\beta\gamma)^!=bc$.
Replacing bosonic statistics by fermionic statistics negates the
central charge: $c_{bc}=-c_{\beta\gamma}$.

\medskip
\noindent\textbf{Modular characteristic and complementarity.}
\[
\kappa(\beta\gamma)
\;=\;
\frac{c_{\beta\gamma}}{2}
\;=\;
6\lambda^2-6\lambda+1,
\qquad
\kappa(bc) = -\kappa(\beta\gamma),
\qquad
\kappa(\beta\gamma)+\kappa(bc)=0.
\]
At $\lambda=1$: $\kappa(\beta\gamma)=1$,
$\kappa(bc)=-1$.

\medskip
\noindent\textbf{Genus-two shell profile.}
\[
\Theta^{(2)}_{\mathrm{loop}\circ\mathrm{loop}}\neq 0,
\qquad
\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}= 0,
\qquad
\Theta^{(2)}_{\mathrm{pf}}= 0.
\]
The sep$\circ$loop shell vanishes because the cubic shadow is zero;
the planted-forest shell vanishes because the contact invariant
$\mu_{\beta\gamma}=0$.  Only iterated curvature contributes at
genus~$2$: the same shell pattern as Heisenberg, but with a different
mechanism (contact termination rather than Gaussian collapse).


% ----- 7.6 Lattice -----
\subsection*{7.6.\quad Lattice vertex algebras}

Lattice vertex algebras are the arithmetic laboratory: the shadow
tower inherits the Gaussian archetype from the Heisenberg factor, but
the braiding carries the full arithmetic of the lattice.  The
curvature sees only the rank; the braiding sees the quadratic form.

Let $\Lambda$ be an even lattice of rank~$N$ with quadratic
form~$q$ and $2$-cocycle~$\varepsilon$.  The lattice vertex algebra
\[
V_\Lambda^{N,q}
\;=\;
\mathcal H_k^{\otimes N}
\;\otimes_{\mathbb C}\;
\mathbb C[\Lambda]_\varepsilon
\]
is the tensor product of the rank-$N$ Heisenberg algebra with the
$\varepsilon$-twisted group algebra of the lattice.  The generators
include the Heisenberg currents $\alpha^i$ ($i=1,\dots,N$) and the
exponential vertex operators $e^{\lambda\cdot\phi}$ for
$\lambda\in\Lambda$.

\medskip
\noindent\textbf{Modular characteristic.}
\[
\kappa(V_\Lambda^{N,q})
\;=\;
\operatorname{rank}(\Lambda)
\;=\;
N,
\]
independent of the cocycle~$\varepsilon$ and the quadratic form~$q$.
The curvature is determined entirely by the Heisenberg part:
the exponential vertex operators $e^{\lambda\cdot\phi}$ contribute to
the braiding but not to the curvature.

\medskip
\noindent\textbf{Curvature-braiding orthogonality.}
The modular curvature class
$[\kappa\cdot\omega_g]\in H^{1,1}(\overline{\mathcal M}_g)$ and the
braiding representation
$\pi_1(\operatorname{Conf}_n(X))\to
\operatorname{Aut}(V_\Lambda^{\otimes n})$
act on complementary factors of the state space.  The curvature sees
$\mathcal H^{\otimes N}$; the braiding sees
$\mathbb C[\Lambda]_\varepsilon$.  The two are orthogonal.

\medskip
\noindent\textbf{Shadow obstruction tower and shells.}
The shadow obstruction tower inherits the Gaussian archetype from the Heisenberg
factor: shadow depth~$2$.  All cubic and higher obstructions vanish.
Genus-two shell profile: loop$\circ$loop only.

\medskip
\noindent\textbf{Special cases.}
The $E_8$ lattice: rank~$8$, self-dual, $\kappa=8$.  The Leech
lattice: rank~$24$, self-dual, $\kappa=24$.  For a self-dual lattice,
$V_\Lambda$ is a holomorphic vertex algebra: the modular functor is
trivial, and the partition function is an honest modular form
(the theta function $\Theta_\Lambda(\tau)/\eta(\tau)^N$).

\medskip
\noindent\textbf{Non-simply-laced algebras.}\enspace
For the non-simply-laced simple Lie algebras $B_2$, $C_2$, $G_2$,
$F_4$: all are class~L (shadow depth~$3$).  The short-root
correction to the Killing form modifies~$\kappa$ by the
lacing number but does not affect the depth classification.
The Langlands dual pair $(B_N, C_N)$ has $\kappa(B_N) \neq
\kappa(C_N)$ but both are class~L: the lacing distinguishes the
scalar invariant but not the structural type.

% ----- 7.7 Yangians -----
\subsection*{7.7.\quad Yangians and quantum groups}

The Yangian is the line-operator algebra: it governs the topological
direction of a holomorphic-topological theory, and its $R$-matrix is
the genus-$0$ binary shadow of the MC element.  The Yang--Baxter
equation is the arity-$3$ MC equation; the RTT relations encode all
arities.

Fix a simple Lie algebra~$\mathfrak g$ of rank~$\ell$.  The Yangian
$Y(\mathfrak g)$ governs the $E_1$-chiral atom: chiral algebras on
ordered configurations in $\mathbb C\times\mathbb R$, where
$\mathbb C$ carries the holomorphic direction and $\mathbb R$ the
topological direction.

\medskip
\noindent\textbf{The $R$-matrix as genus-$0$ binary shadow.}
The $R$-matrix
\[
R(z)
\;=\;
1\;+\;\frac{r}{z}\;+\;\frac{r^{(2)}}{z^2}\;+\;\cdots
\;\in\;
Y(\mathfrak g)\otimes Y(\mathfrak g)[[z^{-1}]]
\]
is the genus-$0$ binary shadow of the MC element:
\[
r(z) \;=\; \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA).
\]
The classical $r$-matrix $r_{\mathrm{cl}}=\Omega/z$ (where
$\Omega=\sum_a J^a\otimes J^a$ is the Casimir tensor) satisfies the
classical Yang--Baxter equation (CYBE):
\[
[r_{12},r_{13}]+[r_{12},r_{23}]+[r_{13},r_{23}] = 0.
\]
This is the Arnold relation on $\operatorname{FM}_3(\mathbb C)$
evaluated on the Casimir: the three terms correspond to the three
boundary divisors of $\overline C_3(\mathbb C)$, and the CYBE is
$d_{\barB}^2=0$ projected to arity~$3$ and genus~$0$.

\medskip
\noindent\textbf{Type-$A$ MC3 reduction.}
On the type-$A$ Yangian surface, the post-CG problem is reduced to a
single remaining compact/completed extension packet.  The reduction
proceeds via:
\begin{enumerate}[label=(\alph*),nosep]
\item \emph{Chromatic filtration.}  Filter
  $K_0(\operatorname{Rep})$ by the support of $q$-characters.  The
  successive quotients are controlled by products of prefundamental
  modules.
\item \emph{Clebsch--Gordan closure.}  The tensor product
  $V_n\otimes L^-=\bigoplus_{j=0}^n L^-(n-2j)$ at character level,
  for all~$n$.  Every Verma character lies in the $K_0$-span of
  $\{[V_n]\cdot[L^-]\}$.
\item \emph{Completion formalism} (more precisely,
  Francis--Gaitsgory pro-nilpotent completion).  Evaluation modules
  are compact, so once an equivalence on the relevant compact core is
  known, it extends to the corresponding ind-completion.  This does
  not by itself supply that compact-core equivalence.
\end{enumerate}
Extension to arbitrary simple type requires the all-types
prefundamental CG package together with the remaining post-CG
extension/completion packets.

\medskip
\noindent\textbf{The dg-shifted Yangian.}
The modular dg-shifted Yangian
$Y_T^{\mathrm{mod}}=\varprojlim_r Y_T^{\mathrm{mod},\le r}$ is the
pronilpotent completion of the convolution dg Lie algebra associated
to the chiral algebra of a 3d holomorphic-topological theory~$T$.
The modular $R$-matrix
\[
R_T^{\mathrm{mod}}(z;\hbar)
\;\in\;
\operatorname{MC}(Y_T^{\mathrm{mod}})
\]
is an MC element.  The Yang--Baxter equation is the MC equation
projected to arity~$3$; the higher RTT relations
$R_{12}R_{13}R_{23}=R_{23}R_{13}R_{12}$ encode the MC equation
at all arities.  The RTT tower is a pro-system of finite-dimensional
MC equations, and the inverse limit converges by Mittag-Leffler
stabilisation: at each finite truncation, the obstruction group is
finite-dimensional and eventually stationary.

\medskip
\noindent\textbf{Drinfeld--Kohno.}
The KZ connection on $\operatorname{Conf}_n(\mathbb C)$ with values
in $\mathfrak g^{\otimes n}$ is
\[
\nabla_{\mathrm{KZ}}
\;=\;
d\;-\;\hbar\sum_{i<j}
\Omega_{ij}\,d\log(z_i-z_j).
\]
Its monodromy representation
$\pi_1(\operatorname{Conf}_n(\mathbb C))\to
\operatorname{Aut}(V^{\otimes n})$
is compared by the affine Drinfeld--Kohno theorem with the
corresponding quantum-group representation category.  In the
shadow obstruction tower:
\[
\nabla_{\mathrm{KZ}}
\;=\;
\operatorname{Sh}_{0,n}(\Theta_{\widehat{\mathfrak g}_k}):
\]
on the affine Kac--Moody comparison surface, the KZ connection is
identified with the genus-$0$ shadow connection determined by the
universal MC element.

\medskip
\noindent\textbf{Shadow obstruction tower.}
The Yangian inherits its shadow structure from the underlying affine
algebra.  At the $E_1$-chiral level, the shadow obstruction tower is controlled
by the $R$-matrix expansion: the arity-$r$ shadow at genus~$0$ is
$r^{(r-1)}/z^{r-1}$, and each coefficient satisfies an RTT-type
constraint.  The genus-$0$ shadow terminates at
depth~$3$ (for class~$\mathbf{L}$ algebras, the CYBE is the full genus-$0$ content at arity~$3$; for class~$\mathbf{M}$, the arity-$3$ MC equation carries strictly more, encoding the homotopy Jacobiator); the modular
extension to genus~$g\ge 1$ requires the completed dg-shifted Yangian
and does not terminate.


\subsection*{7.8.\quad Drinfeld--Sokolov reduction as package morphism}

$\mathrm{DS}\colon\widehat{\mathfrak{sl}}_3{}_k
\to\mathcal W_3{}_{c(k)}$
with $c(k)=2-24(k+2)^2/(k+3)$ extends to a morphism
\[
\mathrm{DS}\colon
\mathcal H(\widehat{\mathfrak{sl}}_3{}_k)
\;\longrightarrow\;
\mathcal H(\mathcal W_3{}_{c(k)})
\]
acting on each component:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lll}
& $\mathcal H(\widehat{\mathfrak{sl}}_3{}_k)$
  & $\mathrm{DS}(\mathcal H)$ \\
\hline
$\cA$ & $\widehat{\mathfrak{sl}}_3{}_k$
  & $\mathcal W_3{}_{c(k)}$ \\
$\cA^!$ & $\widehat{\mathfrak{sl}}_3{}_{-k-6}$
  & $\mathcal W_3{}_{100-c(k)}$ \\
$r(z)$ & $\Omega_{\mathfrak{sl}_3}/z$
  & $r_c^{W_3}(z)$ \\
$\kappa$ & $4(k+3)/3$
  & $5c(k)/6$ \\
depth & $3$
  & $\infty$ \\
$\Theta^{(2)}_{\mathrm{pf}}$ & $0$
  & $\neq 0$
\end{tabular}
\end{center}
\smallskip\noindent
The Casimir $r$-matrix $\Omega/z$ specialises to
$r_c^{W_3}(z)$.  The curvature shifts.  The shadow depth
jumps from $3$ to~$\infty$: DS reduction creates the
planted-forest shell.  The off-diagonal $TW$-mixing in the
genus-$1$ Hessian is the image of the $\mathfrak{sl}_3$ root
structure.  At the critical level $k=-3$:
$\kappa\to 0$ on the affine side (curvature vanishes),
$c\to\infty$ on the $\mathcal W_3$ side (Sugawara pole).

The DS-HPL transfer theorem
(Volume~II, Theorem~thm:ds-hpl-transfer) makes the
chain-level mechanism precise: homological perturbation through
the SDR of the BRST complex transfers the affine dg-shifted
Yangian triple $(m, r, \Delta)$ to the $\mathcal{W}$-algebra side.
The $\Ainf$ products transfer nontrivially (the quartic pole forces
infinite arity), and the $r$-matrix transfers with the expected
pole-order shift.  The coproduct, however, is annihilated: a
ghost-number obstruction kills every HPL tree correction,
so $\Delta_z^{\mathcal{W}} = 0$ at all arities
(Principle~\ref{princ:gravitational-primitivity}).
DS reduction is therefore a functor on modular Koszul triples
(Construction~\ref{constr:ds-functor-triples}), and all
gravitational dynamics resides in the $r$-matrix, not in
coproduct vertices.

\subsection*{Central charge additivity under DS}

The ghost central charge is $k$-independent:
$c_{\mathrm{ghost}} = c(\widehat{\mathfrak{sl}}_3{}_k) - c(\mathcal W_3{}_{c(k)})
= 8k/(k{+}3) - (2 - 24/(k{+}3)) = 6 = 2|\Delta^+(\mathfrak{sl}_3)|$.
The modular characteristics involve different anomaly
ratios: $\kappa(\widehat{\mathfrak{sl}}_3{}_k) = 4(k{+}3)/3$
(Theorem~\ref{thm:genus-universality}),
$\kappa(\mathcal W_3{}_{c(k)}) = 5c(k)/6$, and the deficit
$\kappa_{\mathrm{aff}} - \kappa_{W_3}$ is a rational function
of~$k$
(Proposition~\ref{prop:partition-dependent-complementarity}).
The DS morphism of holographic data is compatible with
the genus expansion at every genus simultaneously, by
functoriality of the graph-sum~\eqref{eq:pref-theta} under DS.

\subsection*{7.9.\quad The geometric localization principle}

The algebraic functoriality above has a geometric substrate.
Drinfeld--Sokolov reduction is not merely an algebraic
construction: it is \emph{Hamiltonian reduction from
$J_\infty(\mathfrak{g}^*)$ to $J_\infty(S_f)$}, where
$S_f = f + \mathfrak{g}^e$ is the Slodowy transverse slice
to the nilpotent orbit of~$f$
(here $\mathfrak{g}^e$ is the centralizer of the nilpotent
element~$e$ in an $\mathfrak{sl}_2$-triple $(e,h,f)$;
Definition~\ref{def:slodowy-slice}).

The Slodowy slice is the universal transverse section through a
nilpotent orbit: it meets every orbit transversally, carries a
Poisson structure from the Kirillov--Kostant bracket, and its
quantization is the finite $W$-algebra
(Gan--Ginzburg~\cite{GanGinzburg02},
Premet~\cite{Premet02}).  The affine/chiral upgrade replaces
$S_f$ by its arc space $J_\infty(S_f)$ (the space of
formal arcs, i.e.\ $\mathbb{C}[\![t]\!]$-points of~$S_f$), and
$\operatorname{gr}_F \mathcal{W}^k(\mathfrak{g},f)
\cong \mathbb{C}[J_\infty(S_f)]$
(Remark~\ref{rem:jet-slodowy}).  In this reading:
\begin{itemize}
\item The PBW--Slodowy collapse
  (Theorem~\ref{thm:w-pbw-slodowy-collapse}) is the algebraic
  expression of \emph{smoothness of the Slodowy slice}
  (Remark~\ref{rem:pbw-slodowy-master-square}).
\item For $\mathcal{W}$-algebras, the shadow depth jump
  $3 \to \infty$ under DS records the \emph{nonlinearity of
  the Dirac bracket} on the arc space $J_\infty(S_f)$: the
  Hamiltonian reduction from the linear Kirillov--Kostant bracket
  on $J_\infty(\mathfrak{g}^*)$ to the nonlinear Dirac bracket
  on $J_\infty(S_f)$ creates the infinite shadow obstruction tower
  (Remark~\ref{rem:ds-depth-increase-geometric}).
\item Barbasch--Vogan orbit duality
  $f \leftrightarrow f^D$, through which the Koszul dual
  orbit is identified, is \emph{Springer duality of Slodowy slices}:
  the curvature complementarity
  $\kappa(\mathcal{W}^k) + \kappa(\mathcal{W}^{k'}) = \mathrm{const}$
  is an algebraic identity under the Feigin--Frenkel involution
  $k + h^\vee \mapsto -(k + h^\vee)$
  (Remark~\ref{rem:bv-springer-duality}).
\item The master commutative square
  (Theorem~\ref{thm:master-commutative-square}) encodes all of
  this: bar complexes on the upper row, Hamiltonian reduction on
  arc spaces on the lower row, PBW identification on the vertical
  arrows.
\end{itemize}


% ====================================================================
\section*{8.\quad The arithmetic of the shadow obstruction tower}
% ====================================================================

The shadow obstruction tower coefficients for the standard families are rational
functions of the central charge.  Their denominators, zeros, and
growth rates carry arithmetic information connecting the shadow
calculus to $L$-functions.  What number-theoretic structures does the MC
equation force?

\subsection*{The Dirichlet--sewing lift}

The genus-$1$ free energy $F_1^{\mathrm{conn}}(\cA;q)
=-\log\det(1-K_q)$, where $K_q$ is the sewing kernel
on $\overline{\cM}_{1,1}$, encodes connected sewing
amplitudes $a_\cA(N)$ as Fourier coefficients.  The
\emph{Dirichlet--sewing lift}
\begin{equation}\label{eq:preface-dirichlet-sewing}
S_\cA(u)
\;:=\;
\sum_{N=1}^\infty a_\cA(N)\,N^{-u}
\;=\;
\frac{(2\pi)^u}{\Gamma(u)}\int_0^\infty
F_\cA^{\mathrm{conn}}(e^{-2\pi y})\,y^{u-1}\,dy
\end{equation}
is a Dirichlet series whose analytic structure is controlled
by the shadow obstruction tower $\Theta_\cA$.  The sewing amplitudes define
an inner product
$\langle f,g\rangle_\cA=\sum_N a_\cA(N)\,f(N)\,g(N)$
on Dirichlet polynomials.  The reproducing kernel
$K_\cA(s,t)=S_\cA(s{+}t)$ is the
\emph{sewing reproducing kernel}, and the surface moment matrix
$\mathscr M_{ij}=K_\cA(\alpha/2{+}i,\,\alpha/2{+}j)$
is positive definite for all $\alpha\geq 2$:
it is a Gram matrix $V^T\!DV$ with Vandermonde~$V$
(Theorem~\ref{thm:gram-positivity}).

Explicit values:
\[
\begin{aligned}
S_{\cH}(u)&=\zeta(u)\,\zeta(u{+}1),\\
S_{V_k(\fg)}(u)&=\dim(\fg)\cdot\zeta(u)\,\zeta(u{+}1),\\
S_{\mathrm{Vir}}(u)&=\zeta(u{+}1)\bigl(\zeta(u)-1\bigr),\\
S_{\mathcal W_N}(u)&=\zeta(u{+}1)\Bigl((N{-}1)\zeta(u)
  -\textstyle\sum_{j=1}^{N-1}H_j(u)\Bigr),
\end{aligned}
\]
where $H_j(u)=\sum_{n=1}^j n^{-u}$ are partial harmonic sums.
The Heisenberg lift is a product of two Riemann zeta functions;
the Virasoro lift subtracts the first Fourier coefficient from
$\zeta$; the $\mathcal W_N$ lifts interpolate via a harmonic sum
that stabilises as $N\to\infty$.

\subsection*{The three-tier Euler--Koszul classification}

The \emph{Euler defect}
$D_\cA(u):=S_\cA(u)\big/(|W(\cA)|\,\zeta(u)\,\zeta(u{+}1))$
classifies chiral algebras into three tiers:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lll}
\textbf{Tier} & \textbf{Condition} & \textbf{Families} \\ \hline
Exact Euler--Koszul & $D_\cA(u)\equiv 1$
  & $\cH$, $V_k(\fg)$, $\beta\gamma$ \\[2pt]
Finitely defective & $1-D_\cA(u)$ is a finite harmonic ratio
  & Virasoro, $\mathcal W_N$ \\[2pt]
Non-Euler--Koszul & $S_\cA$ decomposes into Hecke $L$-functions
  & lattice VOAs with $h(D)\geq 2$
\end{tabular}
\end{center}
The Euler--Koszul class $\mathrm{ek}(\cA)=\max_i(w_i-1)$
and the shadow depth $r_{\max}(\cA)$ are independent invariants
(Theorem~\ref{thm:shadow-euler-independence}):
the first reads the character, the second the OPE.  The two
axes of difficulty, arithmetic (how the coefficients grow)
and algebraic (how the OPE interacts), are logically
independent.

\subsection*{The two-variable $L$-object}

The Rankin--Selberg unfolding against the Eisenstein series
$E^*(\tau,s)$ produces
\begin{equation}\label{eq:preface-two-variable-L}
L_\cA(s,u)
\;:=\;
\int_{\cF}^{\mathrm{reg}}
F_\cA^{\mathrm{conn}}(\tau)\,E^*(\tau,s)\,y^{u-2}\,dx\,dy.
\end{equation}
The \emph{sewing--Hecke reciprocity theorem} collapses the
two variables to one:
$L_\cA(s,u)=\frac{\Gamma(v)}{(2\pi)^v}\,S_\cA(v)$
with $v:=s+u-1$.  Special cases:
the Dirichlet slice $L_\cA(1,u)=\frac{\Gamma(u)}{(2\pi)^u}S_\cA(u)$;
the Selberg slice
$L_\cA(s,0)=\frac{\Gamma(s{-}1)}{(2\pi)^{s-1}}S_\cA(s{-}1)$.
The scattering poles of the Eisenstein series at
$s=\rho/2$ (for nontrivial zeros~$\rho$ of~$\zeta$)
are \emph{not} poles of~$L_\cA$: the Rankin--Selberg
unfolding is holomorphic at these points
(Proposition~\ref{prop:scattering-residue}).
The nontrivial zeros enter as a structural obstruction
to the Euler product, not as poles of the $L$-object.

\subsection*{The shadow-moduli resolution}

The shadow obstruction tower enters the arithmetic through the
\emph{shadow-moduli map} $t\colon\mathfrak H\to\mathbb C$,
solving
\[
\prod_j(1-\lambda_j\,t(q))^{c_j}
\;=\;
\det(1-K_q^{\mathrm{conn}}),
\]
where $\lambda_j$ are the spectral atoms and $c_j$ their
multiplicities.  The connected free energy factors as
$F_1^{\mathrm{conn}}(q;\cA)=G_\cA(t(q))$ with
\[
G_\cA(t)=\int\log(1-\lambda\,t)\,d\rho_\cA(\lambda),
\]
a function determined by the spectral measure~$\rho_\cA$ alone
(Theorem~\ref{thm:universality-of-G}).
The shadow obstruction tower enters as follows: expanding
$G_\cA(t)=-\sum_{r\geq 1}\frac{\mu_r}{r}\,t^r$, the
moments $\mu_r=\int\lambda^r\,d\rho_\cA$ are determined
by the MC equation arity by arity.  At arity~$r{+}1$:
\[
\mu_{r+1}
\;=\;
(r{+}1)\,\operatorname{Br}_{r+1}(\mu_2,\mu_3,\ldots,\mu_r;\cA),
\]
where $\operatorname{Br}_{r+1}$ is a universal polynomial
in the lower moments and the structure constants of~$\cA$
(Proposition~\ref{prop:mc-bracket-determines-atoms}).  For two
Satake-type atoms $\lambda_1=\alpha$, $\lambda_2=\beta$, this
yields, via the Newton relations, a formal spectral polynomial:
the power sums $p_r=e_1\,p_{r-1}-e_2\,p_{r-2}$ encode the MC
recursion in spectral coordinates.

\subsection*{The interacting Gram matrix}

The shadow obstruction tower provides interacting corrections to the
Gram positivity.  The \emph{interacting sewing weight}
\[
w_\cA(N;\alpha)
\;:=\;
a_\cA(N)\cdot\prod_j(1-\lambda_j\,N^{-\alpha/2})^{c_j}
\]
is unconditionally positive when all spectral atoms
$\lambda_j$ are negative
(Theorem~\ref{thm:interacting-gram-positivity}(i)).  The
interacting Gram matrix
$\mathscr M_{ij}^{\mathrm{int}}
=\sum_N w_\cA(N;\alpha)\,N^{-\alpha/2-i}\,N^{-\alpha/2-j}
\succ 0$
in this case.
For Virasoro with $c > 0$: $\lambda_{\mathrm{eff}} = -6/c < 0$,
so positivity holds for all $\alpha \geq 2$ unconditionally
(Corollary~\ref{cor:virasoro-interacting-gram}).
The resonance locus $\mathcal{R}$ is empty for $c > 0$
and confined to the non-unitary regime $c < 0$, with the
Lee--Yang point $c = -22/5$ as the first entry
(Theorem~\ref{thm:shadow-resonance-locus}).

\subsection*{The Weil analogy}

The structural parallel between the MC equation and the Weil
conjectures for curves over finite fields organises the
arithmetic programme:
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{ll}
\textbf{Weil proof for $C/\mathbb F_q$}
  & \textbf{MC equation for~$\cA$} \\ \hline
Curve $C/\mathbb F_q$
  & chirally Koszul algebra $\cA$ \\[2pt]
Frobenius $\mathrm{Frob}_q$
  & MC element $\Theta_\cA=D_\cA-d_0$ \\[2pt]
$\mathrm{Frob}^2=q$ (functional equation)
  & $D_\cA^2=0$ (nilpotence) \\[2pt]
\'Etale cohomology $H^i_{\text{\'et}}$
  & cyclic deformation complex $\Defcyc(\cA)$ \\[2pt]
Weight filtration $W_\bullet$
  & arity filtration $\Theta_\cA^{\leq r}$ \\[2pt]
Eigenvalues $\alpha_i$ on $H^1$
  & spectral atoms $\lambda_j$ of~$\rho_\cA$ \\[2pt]
$\|\alpha_i\|=q^{1/2}$ (Riemann hypothesis)
  & $|a_{f_j}(p)|\leq 2p^{(k-1)/2}$ (Ramanujan) \\[2pt]
Lefschetz operator $L$
  & bracket with $\kappa(\cA)$
\end{tabular}
\end{center}
For even unimodular lattice vertex algebras $V_\Lambda$
with theta series $\Theta_\Lambda
=c_E\,E_{r/2}+\sum_j c_j f_j$ (cusp forms~$f_j$),
the Hecke--Newton closure
(Theorem~\ref{thm:hecke-newton-lattice}) gives the chain:
MC equation $\Rightarrow$ prime-local CG closure
$\Rightarrow$ CPS automorphy $\Rightarrow$
$\operatorname{Sym}^{r-1}(f)$ identification
$\Rightarrow$ Ramanujan bound.
The endpoint recovers the Ramanujan bound for
lattice VOAs
(Corollary~\ref{cor:unconditional-lattice}).
The MC equation supplies the Hecke decomposition and
CPS automorphy; the Ramanujan bound itself follows from
Deligne's theorem on Hecke eigenvalues of cusp
forms~\cite{Deligne1974}, an external input, not
reproved here.  The contribution of the MC framework is
the systematic derivation of the Hecke decomposition
from chiral bar-cobar data, not an independent proof
of the bound.

\subsection*{The Polyakov--bar-cobar dictionary}

The shadow obstruction tower proves Polyakov's worldsheet functional-integral
programme~\cite{Pol87} algebraically:
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{ll}
\textbf{Polyakov object}
  & \textbf{Bar-cobar counterpart} \\ \hline
Conformal anomaly $\langle T^a{}_a\rangle=(c/12)R$
  & modular characteristic $\kappa(\cA)$ \\[2pt]
Functional determinant $\det'_\zeta\Delta$
  & Fredholm $\det(1-K)$ on Bergman kernel \\[2pt]
Critical dimension $c=26$
  & dual characteristic $\kappa(\mathrm{Vir}_{26-c})=0$ \\[2pt]
Ghost system $bc$ ($c_{\mathrm{ghost}}=-26$)
  & Koszul dual $\cA^!$ (BRST pairing, not literal) \\[2pt]
Genus expansion $Z=\sum_g g_s^{2g-2}Z_g$
  & MC5 sewing, $F_g=\kappa\cdot\lambda_g^{\mathrm{FP}}$ (uniform weight) \\[2pt]
BPZ equations (Virasoro degenerate-module surface)
  & shadow connection $\nabla^{\mathrm{sh}}$ on that comparison surface \\[2pt]
Instanton sectors
  & Novikov-completed bar $B^\Lambda(\cA)$ \\[2pt]
Wilson line $\langle W(C)\rangle$
  & Swiss-cheese boundary module
\end{tabular}
\end{center}
The anomaly, the genus expansion, the duality, the critical
dimension, and the non-perturbative completions all descend from
$\Theta_\cA\in\mathrm{MC}(\gAmod)$.  The four shadow depth
classes (Gaussian, Lie, contact, mixed) correspond to increasing
levels of departure from the Gaussian path integral.

The Polyakov dictionary identifies the shadow obstruction tower with the
worldsheet programme at the level of individual objects.  The
following construction upgrades this identification to a connection
on the space of Hecke eigenvalues, providing a differential-geometric
framework for the prime-by-prime structure of the sewing amplitudes.

\subsection*{The arithmetic packet connection}

The Hecke operators $T_p$ ($p$ prime) act on
the space of graph amplitudes
$\ell_\Gamma^{(g)}(\cA)$
through their action on modular forms.
Let $M_\cA$ be the $\bC$-span of the activated amplitudes,
and decompose $M_\cA = \bigoplus_\chi M_\chi$ into
generalised Hecke eigenspaces: on~$M_\chi$, the operator
$T_p$ acts by a scalar $a_\chi(p)$ plus a nilpotent part
$N_\chi$ (the Jordan block defect).  To each eigenspace
attach its \emph{packet function}, the completed
$L$-function of the corresponding eigenform:
for an Eisenstein eigenspace, $\Lambda_0(s) =
C_0(s)\,\zeta(s)\,\zeta(s{-}r/2{+}1)$;
for a cusp eigenspace attached to a normalised eigenform
$f_j$, $\Lambda_j(s) = C_j(s)\,L(s,f_j)$.

The \emph{arithmetic packet connection}
(Definition~\ref{def:arithmetic-packet-connection}) is the
flat meromorphic connection
\[
\nabla_\cA^{\mathrm{arith}}
\;:=\;
d \;-\; \bigoplus_\chi
\frac{\Lambda_\chi'(s)}{\Lambda_\chi(s)}
\bigl(\mathrm{id}_{M_\chi}+N_\chi\bigr)\,ds
\]
on the trivial bundle $M_\cA \otimes \cO_\bC$ over
the spectral line $s \in \bC$.  Flatness is immediate:
on each block, the connection form is a scalar $1$-form
times a constant endomorphism, so both $dA_\chi$ and
$A_\chi \wedge A_\chi$ vanish for degree reasons
(Theorem~\ref{thm:packet-connection-flatness}).
The singular divisor
$D_\cA = \bigcup_\chi \operatorname{div}(\Lambda_\chi)$
is the zero-and-pole set of the packet functions; it
depends only on the semisimple quotient
$M_\cA^{\mathrm{ss}}$ (the \emph{arithmetic skeleton}),
not on the nilpotent parts~$N_\chi$.  The nilpotent
parts produce only unipotent local monodromy
$\exp(2\pi i\,\operatorname{ord}_\rho(\Lambda_\chi)\,
N_\chi)$ around each component of~$D_\cA$
(Theorem~\ref{thm:packet-connection-flatness}(iii)).

The completed Eisenstein scattering function on
$\cM_{1,1}$ is
$\varphi(s) := \Lambda^*(1{-}s)/\Lambda^*(s)$,
where $\Lambda^*(s) = \pi^{-s}\Gamma(s)\zeta(2s)$.
Write $\Lambda_{\mathrm{Eis}}(s) := \Lambda_0(s)$
for the Eisenstein packet.  The \emph{frontier defect
form}
(Definition~\ref{def:frontier-defect-form})
\[
\Omega_\cA
\;:=\;
d\log\Lambda_{\mathrm{Eis}}(s)
\;-\;
d\log\varphi(s)
\]
vanishes iff the Eisenstein block of
$\nabla^{\mathrm{arith}}$ is gauge-equivalent to the
scattering connection $d - d\log\varphi(s)$
(Proposition~\ref{prop:gauge-criterion-scattering};
the additional condition $N_{\mathrm{Eis}} = 0$ is needed
for the gauge to be scalar).
For even unimodular lattice VOAs at rank~$r$:
$\Lambda_{\mathrm{Eis}}(s) = C_0(s)\,\zeta(s)\,\zeta(s{-}r/2{+}1)$,
while $\varphi(s)$ involves $\zeta(2s)/\zeta(2s{-}1)$;
since $\zeta(s)$ and $\zeta(2s)$ have different zero
sets, $\Omega_{V_\Lambda} \neq 0$ in general.

The packet connection treats each algebra uniformly.  For
$\mathcal W_N$ algebras, the DS reduction from affine Kac--Moody
provides additional structure: the Miura transformation splits the
$\mathcal W_N$ character into a Heisenberg core and a finite
correction, isolating all arithmetic content beyond Heisenberg in a
finite product.

\subsection*{The finite Miura defect}

For principal $\cW_N$ with generators of spins
$2,3,\ldots,N$, the $\cW_N$ character is
$\chi_{\cW_N}(q) = \prod_{n \geq 2}
(1 - q^n)^{-\min(n-1,\,N-1)}$
(Proposition~\ref{prop:wn-character-primitive}).
The Heisenberg character is
$\chi_\cH(q) = \prod_{n \geq 1}(1 - q^n)^{-1}$.
The ratio is a finite product
(Theorem~\ref{thm:finite-miura-defect}):
\[
\chi_{\cW_N}(q)
\;=\;
\chi_\cH(q)^{N-1}
\cdot\prod_{m=1}^{N-1}(1-q^m)^{N-m},
\]
since the exponent $(N{-}1) - \min(n{-}1,N{-}1)$
vanishes for $n \geq N$ and equals $N{-}n$ for
$2 \leq n \leq N{-}1$.  The finite product is the
\emph{Miura defect}; all genus-$1$ arithmetic content
in~$\cW_N$ beyond Heisenberg is carried by it.
At the Dirichlet level:
$D_{\cW_N}^{\mathrm{prime}}(u)
= -\zeta(u{+}1)\sum_{m=1}^{N-1}(N{-}m)\,m^{-u}$
(Proposition~\ref{prop:prime-side-defect-formula}).
The packet connection of~$\cW_N$ splits as
$(N{-}1)$ copies of the diagonal Heisenberg connection
$d - d\log[\zeta(s)\zeta(s{+}1)]\,ds$
plus a defect connection governing modes
$m = 1,\ldots,N{-}1$
(Proposition~\ref{prop:miura-packet-splitting}).
The Heisenberg copies contribute only the universal
divisor $\operatorname{div}(\zeta(s))
\cup \operatorname{div}(\zeta(s{+}1))$, and their
contribution to $\Omega_{\cW_N}$ cancels: the frontier
defect form is determined by the defect alone.

The constructions above produce proved arithmetic invariants from the
MC element.  The final programme of this section reverses the
direction: it asks what constraints the nontrivial zeros of
$L$-functions impose on the MC data, through the quartic shadow.

\subsection*{The quartic closure programme}

The quartic resonance class
$\mathfrak{R}_{4,g,n}^{\mathrm{mod}}(\cA)$, the first
nonlinear shadow of~$\Theta_\cA$ (arity~$4$ projection
of the MC element), satisfies a proved clutching law
along every separating boundary stratum
$\xi\colon \overline{\cM}_{g_1,n_1+1} \times
\overline{\cM}_{g_2,n_2+1} \to \overline{\cM}_{g,n}$:
\[
\xi^*\mathfrak{R}_{4,g,n}^{\mathrm{mod}}
\;=\;
p_1^*\mathfrak{R}_{4,g_1,n_1+1}^{\mathrm{mod}}
\;+\;
p_2^*\mathfrak{R}_{4,g_2,n_2+1}^{\mathrm{mod}}
\;+\;
\mathfrak{T}_{3,\xi}
\]
(Theorem~\ref{thm:nms-clutching-law-modular-resonance}).
The $3\times 3$ Schur complement of the mixed
$(s,u)$-transform extracts the quartic contact coupling
$Q_v^{\mathrm{ct}}$ on the potential side and its
reciprocal $(Q_v^{\mathrm{ct}})^{-1}$ on the Gram side
(Theorem~\ref{thm:schur-complement-quartic}).
For Virasoro:
$\Sigma_2^{\mathrm{Vir}} = 10/[c(5c{+}22)]$
(Proposition~\ref{prop:virasoro-quartic-determinant}).

Three closure conjectures form a strict hierarchy
(each implies all predecessors):
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item \emph{quartic closure}
  (Conjecture~\ref{conj:quartic-closure}):
  the intersection of quartic Gram-compatibility loci
  over all families, slices, and regulators is
  $\{\rho : \operatorname{Re}(\rho) = 1/2\}$;
\item \emph{Beilinson closure}
  (Conjecture~\ref{conj:beilinson-closure}):
  the global discrepancy functional $\cB^{\mathrm{glob}}(\rho)$
  vanishes iff $\operatorname{Re}(\rho) = 1/2$;
\item \emph{clutching closure}
  (Conjecture~\ref{conj:clutching-closure}):
  the residue clutching defect $K_{\cA,\rho,\xi}$
  (Definition~\ref{def:residue-clutching-defect})
  vanishes for all families and all boundary strata
  iff $\operatorname{Re}(\rho) = 1/2$.
\end{enumerate}
The chain of constructions:
$\Theta_\cA$ (proved, Theorem~\ref{thm:mc2-bar-intrinsic})
$\to$ residue kernel $w_{c,\rho,u_0}$
(proved, Proposition~\ref{prop:on-off-line-distinction})
$\to$ residue Gram matrix
(Definition~\ref{def:genuine-residue-moment-matrix})
$\to$ Schur complement
(proved, Theorem~\ref{thm:schur-complement-quartic})
$\to$ quartic resonance divisor
(proved, Theorem~\ref{thm:nms-clutching-law-modular-resonance})
$\to$ residue clutching defect
(Definition~\ref{def:residue-clutching-defect})
$\to$ closure conjecture \textup{(conjectural)}.

For lattice vertex algebras, the arithmetic programme has a concrete
incarnation: the bar complex selects a sublattice, and the Epstein
zeta function restricted to that sublattice recovers the Riemann zeta
in the simplest case.

\subsection*{The constrained Epstein zeta}

For a lattice vertex algebra $V_\Lambda$ of rank~$r$,
the \emph{constrained Epstein zeta function}
\[
\varepsilon^c_s(V_\Lambda)
\;:=\;
\sideset{}{'}\sum_{\ell\in\Lambda^{\mathrm{bar}}}
\|\ell\|^{-2s}
\]
restricts the Epstein series to the sublattice
$\Lambda^{\mathrm{bar}}\subset\Lambda$ determined by
the bar complex: the summation runs over those lattice
vectors that contribute nontrivially to the bar
differential.  For the rank-$1$ lattice $V_{\bZ}$
at self-dual radius $R=1$, every nonzero integer
contributes, giving
\[
\varepsilon^1_s(R{=}1) \;=\; 4\,\zeta(2s):
\]
the constrained Epstein zeta of the simplest lattice
VOA \emph{is} the Riemann zeta function (up to the
elementary factor~$4$).

The Hecke operators decompose the constrained series into
$L$-functions:
\[
\varepsilon^r_s(V_\Lambda)
\;=\;
\sum_j c_j\,L(s,\chi_j)
\]
where the sum runs over the Hecke characters~$\chi_j$ of
$\Lambda$ activated by the bar sublattice.  Shadow
depth~$d$ contributes $d-1$ critical lines to the
meromorphic continuation of~$\varepsilon^r_s$, one for
each arity stratum of the shadow obstruction tower beyond the
Gaussian base.  The nontrivial zeros of the
component $L$-functions are the scattering resonances of
the hyperbolic Laplacian on $\cM_{1,1}=\mathrm{SL}(2,\bZ)\backslash\mathfrak H$:
they are the frequencies at which the genus-$1$ sewing
amplitude of~$V_\Lambda$ fails to decay.

\medskip
\noindent\textbf{The B\"ocherer bridge (genus~$2$).}\enspace
At genus~$2$, the shadow tautological class for lattice vertex
algebras computes a central $L$-value via the B\"ocherer conjecture
(Furusawa--Morimoto).  For the Leech lattice $V_\Lambda$ with
$\Lambda = \Lambda_{24}$: the Siegel modular form
$\chi_{12} = \mathrm{SK}(f_{22})$ is the Saito--Kurokawa lift of the
unique weight-$22$ cuspidal eigenform, and the MC-derived second
Fourier coefficient $c_2 \approx -1.918 \times 10^{-6} \neq 0$ is
the first nonzero central $L$-value produced by the shadow obstruction tower,
connecting the MC element $\Theta_\cA$ to the arithmetic of
Siegel modular forms at genus~$2$.

\section*{9.\quad Scalar saturation and the Koszulness programme}
% ====================================================================

The bar construction works for all chiral algebras.  But it works
\emph{best} (the cobar inverts the bar, the spectral sequence
collapses, the resolution is linear) precisely on the Koszul locus.
Characterizing this locus is the central foundational question.  Two
complementary results: scalar saturation (the MC element is determined by a single scalar for
all standard families) and the Koszulness meta-theorem (twelve characterizations, ten unconditionally equivalent, one conditional
on perfectness, one one-directional).

\subsection*{9.1.\quad Scalar saturation}

For a one-parameter algebraic family~$\cA_k$ with rational OPE
coefficients (meaning the structure constants are rational functions
of the level~$k$), the universal MC element satisfies:
\[
\Theta_{\cA_k}
\;=\;
\kappa(\cA_k)\cdot\eta_{\mathrm{univ}}\otimes\Lambda_{\mathrm{univ}}
\;+\;
(\text{terms in $F^3\mathfrak g^{\mathrm{mod}}_{\cA_k}$}).
\]
\emph{Scalar saturation universality}: the higher-order terms vanish.
For every algebraic family with rational OPE coefficients,
$\Theta_{\cA_k}$ is determined by the single scalar
$\kappa(\cA_k)$ modulo terms in the arity-$\ge 3$ filtration.

The proof proceeds in two steps.

\medskip
\noindent\textbf{Step 1: Whitehead reduction.}
For a vertex algebra~$\cA_k$ with reductive symmetry at generic~$k$,
the primitive cyclic cohomology
$H^2_{\mathrm{cyc,prim}}(\mathfrak g^{\mathrm{mod}}/F^3,\,d_2)$ is
computed by a Whitehead-type spectral sequence.  The $E_2$ page is
\[
E_2^{p,q}
\;=\;
H^p\!\bigl(\mathfrak g;\,
\operatorname{Sym}^q V\bigr),
\]
the Lie algebra cohomology of the symmetry algebra acting on the
conformal-weight filtration.  For reductive~$\mathfrak g$ and generic
level, $H^2(\mathfrak g;\operatorname{Sym}^q V)=0$ by the Whitehead
lemma (vanishing of $H^2$ for finite-dimensional semisimple Lie
algebras acting on finite-dimensional modules).  The arity-$2$ MC
class therefore lifts uniquely to the full complex.

\medskip
\noindent\textbf{Step 2: Algebraic semicontinuity.}
The vanishing locus
\[
E \;=\; \bigl\{k\in\mathbb C :
  H^2_{\mathrm{cyc,prim}}(\cA_k)\neq 0\bigr\}
\]
is Zariski-closed in the parameter space (upper semicontinuity of
cohomology dimension as a constructible function).  At the free-field
point $k=\infty$, the algebra is Heisenberg and
$H^2_{\mathrm{cyc,prim}}=0$.  Therefore $E$ is a proper
Zariski-closed subset.  Explicit computation verifies $E=\varnothing$
for $\mathfrak{sl}_N$ ($N=2,\dots,10$): no exceptional level exists.
The result covers the entire standard Lie-theoretic landscape at all
non-critical levels, including admissible ones.

\medskip
\noindent\textbf{Scope.}
Scalar saturation applies to every family in the standard landscape:
affine Kac--Moody (all types, all non-critical levels),
Virasoro (all~$c$), $\mathcal W_N$ (all~$N$, all non-degenerate
levels), $\beta\gamma$ and lattice algebras (all parameters).  The
residual conjecture, that $E=\varnothing$ for \emph{every}
positive-energy chiral algebra with rational OPE coefficients, is
open only for non-algebraic-family constructions (no known counterexample).


\subsection*{9.2.\quad The Koszulness meta-theorem}

The Koszul condition admits twelve formulations,
spanning homological algebra (PBW collapse, Ext vanishing),
homotopy theory ($A_\infty$ formality, $E_2$ formality),
operadic algebra (Barr--Beck--Lurie comparison, FM boundary
acyclicity), modular geometry (FH concentration, tropical
Koszulness), and symplectic topology (Lagrangian criterion).
Ten of these are unconditionally equivalent; one (the Lagrangian
criterion) is conditional on perfectness/nondegeneracy; and one
($\mathcal{D}$-module purity) is one-directional (forward direction
proved, converse open).

The PBW criterion detects Koszulness for every standard family
but does not characterize it intrinsically.
Theorem~\ref{thm:koszul-equivalences-meta}: ten conditions on~$\cA$ are
mutually equivalent, with one conditional on
perfectness and one partial implication.

\medskip
\begin{center}
\emph{For $\cA$ positive-energy and finitely strongly generated,
the following are equivalent:}
\end{center}

\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item $\cA$ is chirally Koszul (Definition~\ref{def:chiral-koszul-morphism}).
\item The PBW spectral sequence on $\barB^{(g)}(\cA)$
  collapses at~$E_2$ for every~$g$.
\item The minimal $A_\infty$-model of $H^\bullet(\barB(\cA))$
  is formal: $m_n = 0$ for $n \geq 3$.
\item $\operatorname{Ext}^{p,q}_\cA(\omega_X, \omega_X) = 0$
  for $p \neq q$ (Ext diagonal vanishing).
\item The bar-cobar counit
  $\Omega(\barB(\cA)) \to \cA$ is a quasi-isomorphism.
\item The Barr--Beck--Lurie comparison for $\barB \dashv \Omega$
  is an equivalence.
\item $\textstyle\int_X \cA$ is concentrated in degree~$0$
  for every smooth proper~$X$.
\item $\mathrm{ChirHoch}^*(\cA)$ vanishes outside degrees
  $\{0,1,2\}$.
\item The Kac--Shapovalov determinant $\det G_h \neq 0$
  in the bar-relevant range.
\item The restriction $i_S^!\,\barB_n(\cA)$ to every FM boundary
  stratum~$S$ is acyclic outside degree~$0$.
\end{enumerate}

\noindent
Under the additional hypothesis that the ambient tangent complex
is perfect and nondegenerate:

\begin{enumerate}[label=\textup{(\roman*)},nosep,start=11]
\item $\mathcal M_\cA$ and $\mathcal M_{\cA^!}$ are transverse
  Lagrangians in the $(-1)$-shifted symplectic deformation
  space $\mathcal M_{\mathrm{comp}}$ (Lagrangian criterion).
\end{enumerate}

\noindent
Finally, (xii)~$\Rightarrow$~(x), where:

\begin{enumerate}[label=\textup{(\roman*)},nosep,start=12]
\item Each $\barB_n(\cA)$ is pure of weight~$n$ as a mixed Hodge
  module, with characteristic variety aligned to FM boundary strata
  ($\mathcal{D}$-module purity).
\end{enumerate}

\noindent
The converse of~(xii) is open.

\medskip
\noindent\textbf{The proof circuit.}
The core equivalence chain is
$\textup{(i)} \Leftrightarrow \textup{(ii)}
\Leftrightarrow \textup{(iii)}
\Leftrightarrow \textup{(v)}
\Leftrightarrow \textup{(viii)}$,
proved by PBW concentration~$\to$ bar-cobar inversion~$\to$ Hochschild
polynomial growth~$\to$ Koszul-complex acyclicity, with the $A_\infty$
formality branch via HPL transfer and Keller classicality.  From this
core, the remaining equivalences follow:
(iv) by Ext spectral sequence,
(vi) by conservativity + log-FM totalization,
(vii) by $\barB = \int_X$,
(ix) by non-degeneracy forcing PBW injectivity,
(x) by stratum-by-stratum PBW concentration.
The Lagrangian criterion~(xi) uses PTVV derived intersection theory
on the perfectness hypothesis.  The $\mathcal{D}$-module purity
implication (xii)$\Rightarrow$(x) uses weight filtration on the bar
complex; the converse would require concentration to force purity.
The cycle closes via
(viii)$\Rightarrow$(i): Koszul-complex acyclicity implies the
defining characterization, completing the equivalence.

\medskip
\noindent\textbf{Beyond the meta-theorem.}
Six additional characterizations are proved in the text, complementing
but not contained in items~(i)--(xii):

\begin{enumerate}[label=\textup{(\alph*)},nosep]
\item \emph{Shadow-formality at low arity.}
  The shadow obstruction tower
  $\Theta^{\le r}_\cA$ equals the $L_\infty$-formality obstruction
  tower of $\mathfrak g^{\mathrm{mod}}_\cA$ at arities $r=2,3,4$
  (Proposition~\ref{prop:shadow-formality-low-arity}).
  At arities $2,3,4$, the shadow obstruction tower \emph{is} the formality
  obstruction tower; full equivalence to~(iii) requires all arities.

\item \emph{$E_2$-formality of chiral Hochschild cohomology.}
  Koszulness implies $\mathrm{ChirHoch}^*(\cA)$ is formal as an
  $E_2$-algebra (Deligne conjecture applied to the bar-cobar
  resolution).  A consequence of~(v), not an independent equivalence.

\item \emph{Genus-$0$ curve independence.}
  Koszulness on~$\mathbb P^1$ implies Koszulness on every smooth
  proper curve
  (Proposition~\ref{prop:genus0-curve-independence}).
  Proved independently by factorization descent.

\item \emph{PBW universality} (sufficient condition).
  Every freely strongly generated vertex algebra is chirally Koszul
  (Proposition~\ref{prop:pbw-universality}; this applies to the
  universal algebra; Koszulness of simple quotients at admissible
  levels is open).
  In particular, $V_k(\mathfrak g)$ is Koszul at \emph{every}
  level~$k$, including critical and admissible.
  This is one-directional: not every Koszul algebra is freely
  strongly generated.

\item \emph{Tropical Koszulness.}
  $\cA$ is chirally Koszul iff $\barB^{\mathrm{trop}}(\cA)$ is
  acyclic (Theorem~\ref{thm:tropical-koszulness}).
  Proved by the weight spectral sequence on the real blowup.

\item \emph{Bifunctor obstruction decomposition} (one-directional).
  Koszulness implies the RNW one-slot obstruction decomposes into
  independent bar-side and cobar-side components
  (Theorem~\ref{thm:bifunctor-obstruction-decomposition}).
  The converse is open.
\end{enumerate}

\medskip
\noindent\textbf{Status summary.}
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{clll}
\multicolumn{4}{l}{\emph{Meta-theorem
  \textup{(}Theorem~\ref{thm:koszul-equivalences-meta}\textup{)}:}}\\[2pt]
& (i)--(x) & \textbf{10 unconditional equivalences} & proved\\
& (xi) Lagrangian & conditional on perfectness & proved
  (unconditional for standard landscape,
  Proposition~\ref{prop:lagrangian-perfectness})\\
& (xii) $\mathcal{D}$-module purity & (xii)$\Rightarrow$(x) only
  & converse open\\[4pt]
\multicolumn{4}{l}{\emph{Additional characterizations:}}\\[2pt]
& (a) Shadow-formality & equivalence at arities $2,3,4$ & proved\\
& (b) $E_2$-formality & consequence of Koszulness & proved\\
& (c) Curve independence & independent theorem & proved\\
& (d) PBW universality & sufficient condition & proved\\
& (e) Tropical Koszulness & equivalence & proved\\
& (f) Bifunctor decomposition & one-directional & converse open
\end{tabular}
\end{center}

\subsection*{9.3.\quad Shadow depth and operadic complexity}

The four depth classes G/L/C/M of \S6.5 admit a refinement.
In general, $r_{\max}$ can take any value in
$\{2,3,4,5,\ldots\}\cup\{\infty\}$: the class $\mathbf{F}_r$
(tower terminates at arity~$r$) is structurally permitted for
all $r \geq 2$, with $\mathbf{G}=\mathbf{F}_2$,
$\mathbf{L}=\mathbf{F}_3$, $\mathbf{C}=\mathbf{F}_4$ naming the
standard-landscape representatives.

\medskip
\noindent\textbf{The operadic complexity theorem.}
The \emph{operadic complexity theorem}
\textup{(}Theorem~\textup{\ref{conj:operadic-complexity-detailed}}\textup{)}
asserts:
\[
r_{\max}(\cA)
\;=\;
A_\infty\text{-depth}(\cA)
\;=\;
L_\infty\text{-formality level}
(\mathfrak g^{\mathrm{mod}}_\cA).
\]
Here $A_\infty$-depth is the minimal~$r$ such that the transferred
$A_\infty$-structure on $H^\bullet(\barB(\cA))$ has $m_k=0$ for all
$k>r$; and $L_\infty$-formality level is the minimal~$r$ such that
the $L_\infty$-structure on $\mathfrak g^{\mathrm{mod}}_\cA$ is
formal through arity~$r$.

The identification has three consequences:
\begin{enumerate}[label=(\roman*),nosep]
\item The shadow obstruction tower \emph{is} the $L_\infty$-formality obstruction
  tower: $\Theta^{\le r}_\cA$ encodes precisely the obstruction to
  $L_\infty$-formality through arity~$r$.
\item The depth classification ($\mathbf{F}_r$ / $\mathbf{M}$)
  becomes a structural invariant of the operadic type of~$\cA$:
  $\mathbf{F}_2$ = free, $\mathbf{F}_3$ = Lie,
  $\mathbf{F}_4$ = quadratic non-Lie, higher $\mathbf{F}_r$ = higher
  non-Lie, $\mathbf{M}$ = genuinely nonlinear.
\item The shadow obstruction tower of a Gaussian algebra is a quadratic form; of a
  Lie algebra, a Chevalley--Eilenberg complex; of a contact algebra, a
  cyclic $A_\infty$-structure; of a mixed algebra, an infinite
  $L_\infty$-tower with no polynomial truncation.
\end{enumerate}


\subsection*{9.4.\quad The PBW spectral sequence}

The computational engine for bar cohomology within each fixed genus
is the PBW (Poincar\'e--Birkhoff--Witt) spectral sequence.  Filter
$\barB^{(g)}(\cA)$ by the \emph{conformal weight}: assign to each
normally ordered monomial in the strong generators its total weight
(the sum of the conformal weights of the constituent fields).  The
associated graded is the bar complex of a free-field algebra, a
computation that reduces to combinatorics of symmetric functions.

The $E_1$ page at genus~$g$ decomposes:
\[
E_1^{p,q}(g)
\;=\;
E_1^{p,q}(g{=}0)
\;\oplus\;
\cE^{p,q}_g,
\]
where the first summand is the genus-$0$ bar cohomology (determined
by Koszulness of the associated graded) and $\cE^{p,q}_g$ is the
genus-$g$ enrichment from the Hodge bundle.  The enrichment at
genus~$g$ arises from the regular Eisenstein series coupled to the
curvature.

\emph{Concentration}: $E_\infty^{p,q}(g)=0$ for $q\neq 0$ at all
genera $g\ge 1$, for all standard families
(Kac--Moody, Virasoro, principal $\mathcal W_N$).  This is PBW
degeneration: the spectral sequence collapses at~$E_2$, and the
bar cohomology is concentrated on the diagonal.

The PBW spectral sequence is \emph{not} the genus spectral sequence
of section~5.5.  The PBW spectral sequence uses conformal weight
within a fixed genus to compute the bar cohomology groups; the genus
spectral sequence uses the genus filtration on the deformation
algebra to control the Maurer--Cartan lift across genera.  One
computes \emph{what}; the other determines \emph{whether}.


\subsection*{9.5.\quad Chiral Hochschild cohomology (Theorem~H)}

The chiral Hochschild complex $\mathrm{ChirHoch}^\bullet(\cA)$ is
the derived endomorphism algebra of the identity functor on
$\cA$-modules, computed by the bar construction with
$\cA$-bimodule coefficients.  At genus~$0$:
\[
\mathrm{ChirHoch}^\bullet(\cA)
\;\simeq\;
R\!\operatorname{Hom}_{\cA\text{-bimod}}(\cA,\cA)
\;\simeq\;
\operatorname{Ext}^\bullet_{\cA^e}(\cA,\cA),
\]
where $\cA^e=\cA\otimes\cA^{\mathrm{op}}$ is the enveloping
chiral algebra.

For $\cA=\mathcal W^k(\mathfrak g,f_{\mathrm{prin}})$ a principal
$\mathcal W$-algebra at generic level:
\[
\mathrm{ChirHoch}^*(\mathcal W^k(\mathfrak g))
\;\cong\;
\mathbb{C}[\Theta_1,\dots,\Theta_r],
\qquad
\deg\Theta_i = m_i+1,
\]
where $m_1,\dots,m_r$ are the exponents of~$\mathfrak g$
and $r = \operatorname{rank}(\mathfrak g)$
(Theorem~\ref{thm:w-algebra-hochschild}).
For $\mathfrak g=\mathfrak{sl}_2$:
$\mathrm{ChirHoch}^*(\mathrm{Vir}_c)=
\mathbb{C}[\Theta]$ with $\deg\Theta=2$
(one polynomial generator, $2$-periodic).
For $\mathfrak g=\mathfrak{sl}_3$:
$\mathrm{ChirHoch}^*(\mathcal W_3)=
\mathbb{C}[\Theta_1,\Theta_2]$ with
generators in degrees $2$ and~$3$.

On the Koszul locus, $\mathrm{ChirHoch}^\bullet(\cA)$ carries an
$E_2$-algebra structure that is formal.  The Connes periodicity
operator $S\colon\mathrm{ChirHoch}^n\to\mathrm{ChirHoch}^{n-2}$
intertwines Koszul duality:
$S\circ\mathrm{KD}=\mathrm{KD}\circ S$.

At genus~$0$, the chiral Hochschild complex identifies with the bulk
chiral homology complex of Volume~II: $\mathrm{ChirHoch}^\bullet(\cA)
\simeq\mathrm{ChirHoch}^\bullet_{\mathrm{bulk}}(\cA)$.
The bulk-boundary-line triangle of section~9.6 is the genus-$0$
shadow of this identification:
$\cA_{\mathrm{bulk}}\simeq Z_{\mathrm{der}}(\cB_\partial)
\simeq\mathrm{ChirHoch}^\bullet(\cA^!)$.


\subsection*{9.6.\quad The shadow algebra}

The \emph{shadow algebra} $\cA^{\mathrm{sh}}$ is the cohomology of
the modular cyclic deformation complex as a graded-commutative ring:
\[
\cA^{\mathrm{sh}}
\;:=\;
H_\bullet\!\bigl(\Defcyc^{\mathrm{mod}}(\cA)\bigr),
\qquad
\cA^{\mathrm{sh}}=\bigoplus_{r\ge 2,\,g\ge 0}
\cA^{\mathrm{sh}}_{r,g}.
\]
The single MC element $\Theta_\cA$ decomposes into components
graded by arity~$r$ and genus~$g$.  Each named shadow is a
projection:
\begin{align*}
\kappa(\cA) &= \cA^{\mathrm{sh}}_{2,0},\\
\mathfrak C(\cA) &= \cA^{\mathrm{sh}}_{3,0},\\
\mathfrak Q(\cA) &= \cA^{\mathrm{sh}}_{4,0},\\
\mathrm{Sh}_r(\cA) &= \cA^{\mathrm{sh}}_{r,0},\qquad r\ge 5.
\end{align*}
The shadow algebra organises the entire hierarchy.  It is a
homotopy invariant of~$\cA$, computed by the Weil homomorphism of
the Chern--Weil dictionary (section~5.4).

The all-arity master equation, read in the shadow algebra, becomes:
$\nabla_H(\mathrm{Sh}_r)+o^{(r)}=0$ for all $r\ge 3$.  The
obstruction class $o^{(r)}$ lies in $\cA^{\mathrm{sh}}_{r,0}$ and
measures the failure of the truncation $\Theta^{\le r-1}_\cA$ to
extend to arity~$r$.


\subsection*{9.7.\quad BV/BRST identification at genus~$0$}

At genus~$0$, the bar differential of a chiral algebra on
$\mathbb C$ is the BRST differential of the associated
holomorphic twist:
\[
(d_{\barB})_{g=0}
\;=\;
Q_{\mathrm{BRST}}.
\]
The bar complex $\barB^{(0)}_{\mathbb C}(\cA)$ is the BRST complex
of the 2d chiral algebra, and bar-cobar inversion
$\Omega(\barB(\cA))\xrightarrow{\sim}\cA$ (Theorem~B) is the
statement that the BRST cohomology, processed through the cobar
functor, reconstructs the original algebra.

At genus~$1$, the identification acquires curvature:
\[
d^2_{\mathrm{fib}}
\;=\;
\kappa(\cA)\cdot\omega_1
\;=\;
\text{one-loop anomaly},
\]
and the curved bar complex is the curved BRST complex of the
theory on an elliptic curve.  The complementarity
$Q_1(\cA)\oplus Q_1(\cA^!)=H^*(\overline{\cM}_{1,1},\cZ_\cA)$
is the genus-$1$ anomaly cancellation condition.

At genus~$g\ge 2$, the identification with the Costello--Gwilliam
BV formalism requires renormalisation: the higher-loop integrals
over $\overline{\cM}_{g,n}$ need regularisation beyond the
algebraic bar-cobar framework, and the correct receptacle is the
coderived category.

The shadow obstruction tower equals the $L_\infty$-formality obstruction
tower at all arities
(Theorem~\ref{thm:shadow-formality-identification}).

\medskip
\noindent\textbf{Genus-two shell activation as depth diagnostic.}
The genus-two shell profile independently confirms the depth
classification:

\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lccc}
& $\Theta^{(2)}_{\mathrm{loop}^2}$
& $\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}$
& $\Theta^{(2)}_{\mathrm{pf}}$\\
\hline
\textbf{G} (Heisenberg, lattice) & $\checkmark$ & --- & ---\\
\textbf{L} (affine $\widehat{\mathfrak g}_k$) & $\checkmark$
  & $\checkmark$ & ---\\
\textbf{C} ($\beta\gamma$) & $\checkmark$ & --- & ---\\
\textbf{M} (Virasoro, $\mathcal W_N$) & $\checkmark$
  & $\checkmark$ & $\checkmark$
\end{tabular}
\end{center}

\noindent
Gaussian and contact algebras activate only the loop$\circ$loop shell;
Lie/tree algebras add the sep$\circ$loop shell; only mixed algebras
activate all three shells including the planted-forest shell.  The
planted-forest shell is the diagnostic: its presence forces infinite
shadow depth.
% ====================================================================
\section*{10.\quad The open/closed world (Volume II)}
% ====================================================================

The bar complex lives naturally in three dimensions.  On the product
$\mathbb C_z \times \mathbb R_t$, the holomorphic direction along
$\mathbb C$ produces the closed-string bar complex of
Sections~1--9: the differential extracts OPE residues from
collisions of points in the holomorphic plane.  The topological
direction along $\mathbb R$ produces the open-string coproduct: the
ordered splitting of tensor factors at a cut point of the real line.
The Swiss-cheese operad encodes the interaction of these two
structures: holomorphic operations acting on the fiber above
the topological interval, topological operations governing the
sequential composition.  The resulting two-colour algebraic
framework is not an embellishment of the bar complex but its
natural habitat: without the topological direction, the coproduct
has no operadic home, and the line-operator category has no
definition.

The primitive object of three-dimensional holomorphic-topological
quantum field theory on $\mathbb C_z \times \mathbb R_t$ is
therefore not the bar complex but the open/closed factorization
dg-category $\mathcal C$ on the bordified curve~$\widetilde{X}_D$.  Its
objects are boundary conditions, its morphisms are open-string
states, and a choice of vacuum~$b$ yields a boundary algebra
$A_b = \operatorname{End}_{\mathcal C}(b)$, determined only up to
Morita equivalence.  The governing operadic structure is the two-coloured
Swiss-cheese operad~$\mathsf{SC}^{\mathrm{ch,top}}$, with closed
colour $\operatorname{FM}_k(\mathbb C)$ and open colour $E_1(m)$,
and it is homotopy-Koszul (proved).

The bar complex of Volume~I is the coalgebraic shadow of this
category: its differential records how closed-sector operations
twist the open-sector composition, and its coproduct records the
ordered splitting of the topological direction.  Together they make
$\barB(\cA)$ a coalgebra over the bar cooperad of the Swiss-cheese
operad.  The bar complex classifies \emph{twisting morphisms},
universal couplings between~$\cA$ and its Koszul dual~$\cA^!$,
and is not the bulk.

Three independent objects are constructed from~$\mathcal C$, and
must never be conflated:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item the \emph{bar complex} $\barB(A_b)$ classifies couplings
  between $A_b$ and~$A_b^!$;
\item the \emph{chiral derived center}
  $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\mathcal C) =
  R\!\operatorname{Hom}_{\operatorname{Fun}(\mathcal C,\mathcal C)}
  (\operatorname{Id}, \operatorname{Id})$
  is the universal bulk, computed in any chart by chiral Hochschild
  cochains $C^\bullet_{\mathrm{ch}}(A_b, A_b)$;
\item the \emph{Koszul dual} $A_b^!$ governs the line-operator
  category.
\end{enumerate}
The primitive hierarchy is:
\[
\mathcal C_{\mathrm{op}}
\;\xrightarrow{\;\operatorname{End}(b)\;}
A_b
\;\xrightarrow{\;\barB\;}
\barB(A_b)
\;\xrightarrow{\;\Theta\;}
\Theta_\cA
\;\xrightarrow{\;+\mu^{M_j}\;}
\Theta^{\mathrm{oc}}_\cA.
\]
Each arrow is a lossy functor: $\mathcal C_{\mathrm{op}}$ is
Morita-invariant; $A_b$ depends on the choice of boundary
condition~$b$; $\barB$ forgets the bulk; $\Theta_\cA$ is the
closed-sector MC element; $\Theta^{\mathrm{oc}}_\cA$ restores the
full open/closed package.
Modularity is determined by the open sector: a cyclic trace on
$\operatorname{End}(b)$ seeds the Calabi--Yau structure; the
annulus identification
$\int_{S^1} \mathcal C \simeq \operatorname{HH}_\bullet(\mathcal C)$
is the first modular shadow; clutching (composing along
boundary circles via nodal degeneration) raises genus.
The genus expansion of
$\Theta^{\mathrm{oc}}_\cA$ yields the perturbative free energies
$F_g$; the shadow archetypes
$\mathsf{G}/\mathsf{L}/\mathsf{C}/\mathsf{M}$
classify the nonlinear complexity of the Swiss-cheese operations.

Volume~II constructs this architecture in four stages:
\emph{Stage~1} (local one-colour theorem: Swiss-cheese
universality of the derived center) $\Rightarrow$
\emph{Stage~2} (open primitive: $\mathcal C$ with Morita
invariance) $\Rightarrow$
\emph{Stage~3} (globalization on tangential log curves
$(X,D,\tau)$) $\Rightarrow$
\emph{Stage~4} (modularization: trace plus clutching producing
$\Theta^{\mathrm{oc}}$).
Stages~1--3 are proved.  In Stage~4, the open/closed MC element
$\Theta^{\mathrm{oc}}_\cA$ is constructed, the modular
MC equation holds at all genera
(Theorem~\ref{thm:thqg-oc-mc-equation}), and the
projection principle recovers both the closed-sector genus
tower and the open-sector module structures
(Theorem~\ref{thm:thqg-oc-projection}).
The annulus trace is proved
(Theorem~\ref{thm:thqg-annulus-trace}).
The independent open-sector derivation of higher-genus
amplitudes and the chain-level cooperad compatibilities remain
open.

\subsection*{10.1.\enspace The holomorphic-topological Swiss-cheese operad}

The \emph{holomorphic-topological Swiss-cheese operad}
$\mathsf{SC}^{\mathrm{ch,top}}$ is a two-colored operad with color
set $\{\mathrm{ch},\mathrm{top}\}$.  The color $\mathrm{ch}$ is
\emph{closed} (holomorphic); the color $\mathrm{top}$ is
\emph{open} (topological).  The operation spaces are:
\begin{align*}
\mathsf{SC}(\mathrm{ch}^k;\mathrm{ch})
&=\operatorname{FM}_k(\mathbb C),\\
\mathsf{SC}(\mathrm{ch}^k,\mathrm{top}^m;\mathrm{top})
&=\operatorname{FM}_k(\mathbb C)\times E_1(m),\\
\mathsf{SC}(\ldots,\mathrm{top},\ldots;\mathrm{ch})
&=\varnothing.
\end{align*}
Closed-to-closed is the Fulton--MacPherson
compactification of configuration spaces in~$\mathbb C$.
The mixed direction combines holomorphic
configurations with the $E_1$-operad: $k$
holomorphic and $m$ topological insertion points,
with holomorphic insertions acting on the fiber above the interval.
Open-to-closed is forbidden.

Operadic composition is determined by the boundary stratification of
FM spaces in the holomorphic direction and by nested interval
inclusions in the topological direction.  If $\sigma_S$ denotes
the boundary stratum of $\operatorname{FM}_k(\mathbb C)$
corresponding to the simultaneous collision of the subset
$S\subset\{1,\ldots,k\}$, then the operadic composition map
$\gamma_{S}$ is the inclusion of the fiber product
\[
\gamma_S\colon
\operatorname{FM}_{|S|}(\mathbb C)\times\operatorname{FM}_{k-|S|+1}(\mathbb C)
\;\hookrightarrow\;
\operatorname{FM}_k(\mathbb C)
\]
as the normal bundle of~$\sigma_S$.  In the topological direction,
$E_1$-composition is the standard operadic substitution of intervals
into intervals.

A bar element of tensor degree~$k$ lives on the product
$\operatorname{FM}_k(\mathbb C)\times\operatorname{Conf}_k(\mathbb R)$.
The bar differential extracts OPE residues along collision divisors
of the first factor: when points $z_i$ and $z_j$ collide, the
residue of the propagator $\eta_{ij}=d\log(z_i-z_j)$ against the
collision divisor $\sigma_{\{i,j\}}$ yields the OPE mode
$a_{(n)}b$.  The coproduct splits an ordered sequence of tensor
factors at a point of the second factor: an element
$a_1\otimes\cdots\otimes a_k$ with ordering
$t_1<\cdots<t_k$ on $\mathbb R$ is decomposed at a cut point
$t_p<c<t_{p+1}$ into
$(a_1\otimes\cdots\otimes a_p)\otimes(a_{p+1}\otimes\cdots\otimes a_k)$.
The bar complex carrying both structures is an
$\mathsf{SC}^{\mathrm{ch,top}}$-algebra.

\subsection*{10.2.\enspace Homotopy-Koszulity of $\mathsf{SC}^{\mathrm{ch,top}}$}

The classical Swiss-cheese operad $\mathsf{SC}$ is Koszul
(Livernet, Voronov; Ginzburg--Kapranov).  The proof: the
Koszul dual cooperad $\mathsf{SC}^{\text{\raisebox{0.3ex}{!`}}}$
has a quadratic presentation, and the bar-cobar resolution is a
quasi-isomorphism by the combinatorial criterion of distributive
lattices applied to the poset of nested disks.  Kontsevich formality
supplies a quasi-isomorphism
\[
\Phi\colon\mathsf{SC}^{\mathrm{ch,top}}
\;\xrightarrow{\;\sim\;}\;
\mathsf{SC}
\]
constructed from Kontsevich's formality morphism for the $E_2$-operad
(configuration space integrals on FM spaces with propagators), extended
to the Swiss-cheese setting by including the half-plane $\mathbb H$
and its boundary $\mathbb R$.  The bar-cobar adjunction preserves
quasi-isomorphisms by the standard filtration-spectral-sequence
argument on the cobar side; the two-out-of-three property in the
model category of operads then gives
\[
\Omega\mathbf B(\mathsf{SC}^{\mathrm{ch,top}})
\;\xrightarrow{\;\sim\;}\;
\mathsf{SC}^{\mathrm{ch,top}}.
\]
The bar-cobar adjunction on
$\mathsf{SC}^{\mathrm{ch,top}}$-algebras is therefore a
\emph{Quillen equivalence}: the derived unit and counit are both
weak equivalences.  This has three consequences:
\begin{enumerate}[label=(\roman*),nosep]
\item Every $\mathsf{SC}^{\mathrm{ch,top}}$-algebra admits a
  cofibrant replacement by a bar-cobar resolution.
\item The homotopy category of
  $\mathsf{SC}^{\mathrm{ch,top}}$-algebras is equivalent to the
  homotopy category of coalgebras over the Koszul dual cooperad.
\item The line-operator category $\cA^!\text{-}\mathsf{mod}$ is
  unconditionally defined as a module category over the bar
  resolution, without any finiteness hypothesis on~$\cA$.
\end{enumerate}

\subsection*{10.3.\enspace The $A_\infty$ chiral algebra structure}

The full Swiss-cheese MC element
$\alpha_T \in \operatorname{MC}(\mathfrak{g}^{\mathrm{SC}}_T)$
lives in the Swiss-cheese convolution algebra
$\mathfrak{g}^{\mathrm{SC}}_T :=
\operatorname{Hom}_\Sigma\bigl(
\mathbf{B}(\mathsf{SC}^{\mathrm{ch,top}}),
\operatorname{End}_{(B_\partial,\,\mathcal{C}_{\mathrm{line}})}\bigr)$.
Its closed-colour projection $(m_k)_{k\ge 1}$
encodes the $A_\infty$ chiral algebra on~$\cA$.  Each component
\[
m_k\colon\cA^{\otimes k}
\;\longrightarrow\;
\cA((\lambda_1))\cdots((\lambda_{k-1}))
\]
is a configuration-space integral on
$\operatorname{FM}_k(\mathbb C)\times\operatorname{Conf}_k(\mathbb R)$.
Write $\omega_I$ for the form on $\operatorname{FM}_k(\mathbb C)$
obtained by wedging the propagators $\eta_{ij}=d\log(z_i-z_j)$
for all pairs $(i,j)\in I$.  The holomorphic factor produces the
OPE singularity; the topological factor produces the ordering.
Explicitly, $m_k$ at arity $k$ is the sum over trees $T$ with $k$
leaves of
\[
m_T(a_1,\ldots,a_k)
\;=\;
\int_{\operatorname{FM}_k(\mathbb C)}
\omega_T\,\cdot\,
\prod_{v\in V(T)} a_{(n_v)} b_v\,,
\]
where the integration is against the compactified configuration
space volume form and the product is over internal vertices of~$T$
with the OPE modes prescribed by the edge labels.

The Maurer--Cartan equation
$\partial\alpha+\alpha\star\alpha=0$ is the \emph{spectral Stasheff
identity}.  Integration over the boundary strata of
$\operatorname{FM}_k(\mathbb C)$ produces the $A_\infty$ relations
by Stokes' theorem:
\[
\sum_{\substack{p+q=k+1\\1\le i\le p}}
\pm\,m_p(a_1,\ldots,a_{i-1},\,m_q(a_i,\ldots,a_{i+q-1}),\,a_{i+q},\ldots,a_k)
\;=\;0.
\]
Each term in this identity corresponds to a codimension-one
boundary stratum of $\operatorname{FM}_k(\mathbb C)$ where a
subset of points collides: the inner $m_q$ extracts the OPE from
the collision, and the outer $m_p$ evaluates the remaining
configuration.

\subsection*{10.4.\enspace PVA descent: Theorem G}

On cohomology $H^\bullet(\cA,Q)$, the operations simplify by a
dimension count.

\medskip
\noindent\emph{The commutative product.}
The regular part of~$m_2$, the constant term as the two points
separate, is a commutative associative product~$\mu$:
\[
\mu(a,b)
\;=\;
\operatorname{Reg}_{z_1\to z_2}\,m_2(a(z_1),b(z_2)).
\]
Commutativity: $\operatorname{FM}_2(\mathbb C)$ has a $\mathbb Z/2$
involution exchanging the two points; the regular part is invariant.
Associativity: the three boundary strata of
$\operatorname{FM}_3(\mathbb C)$ corresponding to pairwise
collisions contribute only to the singular part; the regular
boundary term is associativity.

\medskip
\noindent\emph{The $\lambda$-bracket.}
The singular part of~$m_2$ defines the $\lambda$-bracket:
\[
\{a_\lambda b\}
\;=\;
\operatorname{Res}_{z_1\to z_2}\,
e^{\lambda(z_1-z_2)}\,
m_2(a(z_1),b(z_2)).
\]
The exponential extracts all pole orders simultaneously:
$\{a_\lambda b\}=\sum_{n\ge 0}\lambda^n a_{(n)}b/n!$.

\medskip
\noindent\emph{Vanishing of higher operations.}
All $m_{k\ge 3}=0$ on $H^\bullet$: the topological factor
$\operatorname{Conf}_k(\mathbb R)$ is contractible for $k\ge 3$
(it retracts to a point by pulling all $k$ ordered points together),
so the cohomological representative of $m_k$ is $d_{\mathbb R}$-exact
and therefore trivial on $H^\bullet$.

\medskip
\noindent\emph{Jacobi identity from the Arnold relation.}
On $\operatorname{FM}_3(\mathbb C)$, the three propagators
$\eta_{12}$, $\eta_{23}$, $\eta_{31}$ satisfy the Arnold relation:
\[
\eta_{12}\wedge\eta_{23}
\;+\;
\eta_{23}\wedge\eta_{31}
\;+\;
\eta_{31}\wedge\eta_{12}
\;=\;0.
\]
This identity on differential forms is equivalent to the three
codimension-one boundary divisors of $\overline M_{0,4}$ being
homologous to zero in sum.  Taking the residue of this relation
against $a\otimes b\otimes c$ produces the three terms of the
Jacobi identity for $\{-_\lambda-\}$:
\[
\{a_\lambda\{b_\mu c\}\}
\;-\;
\{b_\mu\{a_\lambda c\}\}
\;=\;
\{\{a_\lambda b\}_{\lambda+\mu}c\}.
\]

\medskip
\noindent\emph{Leibniz rule from three-face Stokes.}
The boundary of $\operatorname{FM}_3(\mathbb C)$ decomposes into
three codimension-one faces, each corresponding to a pairwise
collision.  The Stokes identity
\[
\int_{\partial\operatorname{FM}_3(\mathbb C)}\omega
\;=\;
\int_{\sigma_{12}}\omega
\;+\;
\int_{\sigma_{23}}\omega
\;+\;
\int_{\sigma_{13}}\omega
\;=\;0
\]
applied to the form
$\omega=\eta_{12}\wedge\eta_{23}\cdot a(z_1)b(z_2)c(z_3)$
gives: on~$\sigma_{12}$, the bracket $\{a_\lambda b\}$ is formed
first and then multiplied by~$c$; on~$\sigma_{23}$,
$a$ multiplied by $\{b_\lambda c\}$; on~$\sigma_{13}$,
$\{a_\lambda c\}\cdot b$.  The cancellation is the Leibniz rule:
\[
\{a_\lambda(b\cdot c)\}
\;=\;
\{a_\lambda b\}\cdot c
\;+\;
b\cdot\{a_\lambda c\}.
\]

\medskip
\noindent\emph{Skew-symmetry from the exchange cylinder.}
The exchange involution on
$\operatorname{FM}_2(\mathbb C)\times E_1(2)$ swaps the two
insertion points.  The monodromy of $\eta_{12}$ around the exchange
loop in the $E_1$ direction produces a sign and a shift:
$\{a_\lambda b\}=-\{b_{-\lambda-\partial}a\}$.  The derivative
$\partial$ appears because the exchange path on $E_1(2)$ winds
once around the difference coordinate $z_1-z_2$.

\medskip
\noindent
Thus $(\mu,\{-_\lambda-\})$ is a $(-1)$-shifted Poisson
vertex algebra, each axiom following in one line from the
geometry of $\operatorname{FM}_k(\mathbb C)$.

\subsection*{10.5.\enspace The Heisenberg algebra in Swiss-cheese coordinates}

For the Heisenberg algebra $\mathcal H_k$, generated by a
single field $J$ of conformal weight~$1$ with
$J(z)J(w)\sim k/(z-w)^2$:
\[
m_2(J,J)=k\cdot\mathbf{1},
\qquad
m_{k\ge 3}=0,
\qquad
\{J_\lambda J\}=k\lambda.
\]
All higher operations vanish because the OPE has no first-order
pole: the only nontrivial residue is $J_{(1)}J=k$, and
configuration-space integrals at arity $k\ge 3$ factor through
this single datum, yielding zero by degree considerations
(the form $\eta_{12}\wedge\cdots$ has too high a degree to pair
nontrivially with the rank-one OPE data).  The spectral
$R$-matrix is
\[
R(z)\;=\;\exp(k/z).
\]
The Yang--Baxter equation is trivially satisfied: the $R$-matrix is
scalar (acting on $\mathbb C\otimes\mathbb C$), so both sides of
the YBE are $\exp(k/z_{12}+k/z_{13}+k/z_{23})$.  The PVA
$\{J_\lambda J\}=k\lambda$ is the free bosonic PVA, the universal
enveloping PVA of the rank-one abelian Lie conformal algebra.

\subsection*{10.6.\enspace The Koszul triangle}

The open factorization dg-category $\mathcal C$ on
$\widetilde{X}_D$ produces three independent algebraic objects,
each by a different functor:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item \emph{Boundary.}  $A_b = \operatorname{End}_{\mathcal C}(b)$
  for a chosen vacuum object~$b$: an algebra over the open colour
  of $\mathsf{SC}^{\mathrm{ch,top}}$, encoding the
  $E_1$-composition.  The boundary algebra is a \emph{chart} on
  $\mathcal C$, determined up to Morita equivalence by the choice
  of~$b$.
\item \emph{Bulk.}
  $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\mathcal C)
  = R\!\operatorname{Hom}_{\operatorname{Fun}(\mathcal C,\mathcal C)}
  (\operatorname{Id}, \operatorname{Id})$:
  the chiral derived center, the universal algebra of bulk
  operators.  It is Morita-invariant, independent of the choice
  of~$b$.  In any chart it is computed by chiral Hochschild
  cochains $C^\bullet_{\mathrm{ch}}(A_b, A_b)$.
\item \emph{Lines.}
  $A_b^{!}{}_\infty = D_{\operatorname{Ran}}(\barB(A_b))$: the
  \emph{homotopy} Koszul dual, obtained by Verdier duality on the
  bar coalgebra.  On the Koszul locus, its cohomology recovers the
  strict Koszul dual $A_b^! = (H^*(\barB(A_b)))^\vee$ (Theorem~A).
  The module category $A_b^!\text{-}\mathsf{mod}$, equipped with
  the spectral $R$-matrix~$R(z)$, is the braided tensor category
  of line operators.
\end{enumerate}
The three objects are related by a triangle of identifications
\[
\cZ^{\mathrm{der}}_{\mathrm{ch}}(\mathcal C)
\;\simeq\;
\operatorname{HH}^\bullet(A_b)
\;\simeq\;
\mathrm{ChirHoch}^\bullet(A_b^!),
\qquad
A_b^!\text{-}\mathsf{mod}\;=\;\{\text{line operators}\},
\]
but the three functors (endomorphisms, Ran-space Verdier
duality, identity-bimodule endomorphisms) must never be
conflated.  In particular: the bar complex $\barB(A_b)$ classifies
twisting morphisms (universal couplings between $A_b$ and~$A_b^!$)
and is not the bulk.  The derived center classifies bulk operators
acting on the boundary.

\medskip
\noindent\emph{The spectral braiding.}
The $R$-matrix $R(z)\colon L_1\otimes L_2\xrightarrow{\sim}
L_2\otimes L_1$ is the spectral braiding on $\cA^!$-modules.
Stokes' theorem on $\operatorname{FM}_3(\mathbb C)$ applied to
the triple convolution $\alpha\star\alpha\star\alpha$ decomposes
the boundary into three pairwise collision divisors, one for
each side of the Yang--Baxter equation:
\[
R_{12}(z_1{-}z_2)\,R_{13}(z_1{-}z_3)\,R_{23}(z_2{-}z_3)
\;=\;
R_{23}(z_2{-}z_3)\,R_{13}(z_1{-}z_3)\,R_{12}(z_1{-}z_2).
\]
The three boundary strata of $\operatorname{FM}_3(\mathbb C)$ are
in bijection with the three channels $(12|3)$, $(13|2)$,
$(23|1)$; the Stokes cancellation
$\sum_{\sigma}\int_{\sigma}\omega=0$ is precisely the YBE.

\medskip
\noindent\emph{Bulk = derived center.}
Let $\cB_\partial$ be the boundary factorization algebra on
$\mathbb R$ (the open/topological algebra of the SC structure).
Its derived center
$Z_{\mathrm{der}}(\cB_\partial)
:=R\operatorname{Hom}_{\cB_\partial\text{-}\mathrm{bimod}}
(\cB_\partial,\cB_\partial)$
computes endomorphisms of the identity bimodule.  The $E_1$-structure
on $\cB_\partial$ gives
$Z_{\mathrm{der}}(\cB_\partial)\simeq\mathrm{HH}^\bullet(\cB_\partial)$
as an $E_2$-algebra.  The Swiss-cheese structure maps the holomorphic
bulk algebra to this $E_2$-algebra, and the Quillen equivalence
makes the map an equivalence.

\medskip
\noindent\emph{Lines = $\cA^!$-modules.}
An $\cA^!$-module~$M$ defines a line operator: the module
structure $\cA^!\otimes M\to M$ is a topological boundary
condition parametrised by a line in $\mathbb R$, and the spectral
braiding $R(z)$ provides the crossing data when two lines
intersect.  The category $\cC:=\cA^!\text{-}\mathsf{mod}$ with
braiding $R(z)$ is the braided tensor category of line operators
of the 3d holomorphic-topological theory.

\subsection*{10.7.\enspace Curved Swiss-cheese at genus $g\ge 1$}

At genus $g\ge 1$, the bar complex
$(\bar B^{\mathrm{ch},(g)}(\cA),\,d_{\mathrm{fib}},\,\Delta)$
carries curvature:
\[
d_{\mathrm{fib}}^{\,2}\;=\;\kappa(\cA)\cdot\omega_g.
\]
The curvature $\omega_g$ is the Arakelov $(1,1)$-form on the fiber
of the universal curve $\pi\colon\cC_g\to\overline{\cM}_g$,
representing the first Chern class of the relative dualising sheaf.
The coproduct~$\Delta$ remains strictly coassociative: the
topological $E_1$-structure on $\mathbb R$ sees no curvature
(the interval has no nontrivial topology).  The curvature lives
entirely in the holomorphic direction.

The total corrected differential
\[
D_g\;=\;d_{\mathrm{fib}}+\nabla^{\mathrm{GM}}_g
\]
restores flatness over $\overline{\cM}_g$ by coupling the
$\mathbb R$-ordering to the Hodge bundle~$\mathbb E$.  The
Gauss--Manin connection $\nabla^{\mathrm{GM}}$ absorbs the
$(1,1)$-curvature: $D_g^{\,2}=0$ because
$d_{\mathrm{fib}}^{\,2}+[d_{\mathrm{fib}},\nabla^{\mathrm{GM}}]
+(\nabla^{\mathrm{GM}})^2=\kappa\omega_g-\kappa\omega_g=0$.

The derived category of modules must be replaced by the
\emph{coderived} category $\mathsf{D}^{\mathrm{co}}(\cA^{(g)})$
(or the contraderived category
$\mathsf{D}^{\mathrm{ctr}}(\cA^{(g)})$, depending on the side):
curvature forces $d^2\neq 0$ on fibers, so the ordinary derived
category is empty (every object is acyclic), while the coderived
category, defined via totalisation of the curvature bicomplex,
retains the correct homotopy theory.  The passage from derived
to coderived is the categorified form of the passage from
$d^2=0$ to the curved Maurer--Cartan equation
$d\alpha+\alpha^2+\kappa\omega=0$.

\subsection*{10.8.\enspace The Lagrangian self-intersection}

Volume~II identifies the geometric substrate of the bar construction:
the bar complex is the structure sheaf of the Lagrangian
self-intersection
$\mathfrak{S} = \mathcal{L} \times_{\mathcal{M}} \mathcal{L}$
in a $(-2)$-shifted symplectic stack, and every theorem of this
volume is a face of that geometry.
The bar-cobar adjunction (Theorem~A) is the groupoid
comodule-module adjunction for~$\mathfrak{S}$;
Koszul inversion (Theorem~B) reconstructs the Lagrangian from
its clean self-intersection;
complementarity (Theorem~C) is two Lagrangians whose intersection
carries a $(-1)$-shifted symplectic structure;
the modular characteristic (Theorem~D) is the Kodaira--Spencer
class of the Lagrangian family over the Hodge bundle;
and the Hochschild polynomial growth (Theorem~H) is the HKR
theorem for the Lagrangian embedding.

\subsection*{10.9.\enspace The factorization-primary hierarchy}

The Swiss-cheese operad $\mathsf{SC}^{\mathrm{ch,top}}$ is a
\emph{local model}: the formal completion of a factorization
structure at collision points.  The global truth is a factorizable
$\mathcal D$-module on $\operatorname{Ran}(\Sigma_g)$ (the Ran
space of finite non-empty subsets of the curve), varying in families
over~$\overline{\cM}_g$.  The operad is extracted from this by
restricting to formal neighborhoods of the small diagonal, where
$\Sigma_g \simeq \mathbb C$ and the factorization pattern reduces
to FM-space operations.  Six layers organise the hierarchy:
\begin{enumerate}[label=(\roman*),nosep]
\item \emph{Geometric substrate:} smooth and stable nodal curves,
  Ran space, $\overline{\cM}_{g,n}$.
\item \emph{Factorizable $\mathcal D$-modules} (Beilinson--Drinfeld):
  a chiral algebra is a factorizable $\mathcal D$-module on
  $\operatorname{Ran}(X)$, not an algebra over an operad.
\item \emph{HT product geometry:} $\Sigma_g \times \mathbb R$ with
  holomorphic factorization in~$\Sigma_g$ and locally constant
  factorization in~$\mathbb R$.
\item \emph{Bar as factorization coalgebra:} the bar complex is the
  factorization coalgebra on $\operatorname{Ran}(X)$ Koszul-dual to
  the chiral algebra.  At genus~$0$: honest dg coalgebra.  At
  genus~$g \ge 1$: curved factorization coalgebra.
\item \emph{Koszul duality as factorization duality:} bar-cobar is
  factorization algebra $\leftrightarrow$ coalgebra duality.
  Feynman involution $\mathrm{FT}^2 \simeq \mathrm{id}$ is the
  involutivity of this duality.
\item \emph{Three models as three gauges:} the flat associated graded
  ($D_0^2 = 0$, operadic/local), the corrected holomorphic
  ($D^{(g)\,2} = 0$, Fay trisecant, still local), and the curved
  geometric ($d_{\mathrm{fib}}^2 = \kappa \cdot \omega_g$, Arakelov,
  global).  The corrected model is visible to the local operad; the
  curved model requires the factorization framework.
\end{enumerate}
The curvature $d_{\mathrm{fib}}^2 = \kappa \cdot \omega_g$ is the
measure of what the local extraction loses: it is the monodromy of
the $\mathcal D$-module connection around the $B$-cycles of
$\Sigma_g$, invisible to the formal-disc model.  The modular bar
complex $\barB_{\mathrm{mod}}(\cA)$ is flat ($D^2 = 0$) because it
couples all genera simultaneously via the non-separating operator
$D_1$; the genus-$g$ bar complex on a fixed surface is curved
because restricting to a single genus decouples this connection.

The relative Feynman transform
$\mathrm{FT}_{\mathsf{Com}_{\mathrm{mod}}/\mathsf{SC}^{\mathrm{ch,top}}}$
mediates between the factorization (global) and operadic (local)
viewpoints.  The modular bar coalgebra is naturally an algebra over
this relative transform.  Relative homotopy-involutivity plus
factorization Koszul duality gives the flat-derived /
curved-coderived comparison at all genera: the two flat models share
an ordinary derived package, while the genus-fixed curved model is
its coderived avatar rather than a third ordinary chain complex.

\subsection*{10.10.\enspace The four-stage architecture}

Four stages, each depending on its predecessor.

\medskip
\noindent
\emph{Stage~1: Local one-colour theorem.}
The Swiss-cheese operad $\mathsf{SC}^{\mathrm{ch,top}}$ is
homotopy-Koszul; the resulting bar-cobar adjunction is a Quillen
equivalence.  The chiral derived center
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\mathcal C)
\simeq C^\bullet_{\mathrm{ch}}(A_b, A_b)$
is the universal bulk algebra.  \textsc{Proved.}

\medskip
\noindent
\emph{Stage~2: Open primitive.}
The primitive object is the open factorization dg-category
$\mathcal C$.  The boundary algebra
$A_b = \operatorname{End}_{\mathcal C}(b)$ is a chart, not an
essence; the bulk $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\mathcal C)$
is Morita-invariant.  \textsc{Proved.}

\medskip
\noindent
\emph{Stage~3: Globalization.}
Tangential log curves $(X,D,\tau)$ provide the geometric substrate
for bordered Fulton--MacPherson compactification.  The local-global
bridge lifts the operad-level Swiss-cheese structure to a
factorizable $\mathcal D$-module on $\operatorname{Ran}(X)$.
\textsc{Proved locally; modest globally.}

\medskip
\noindent
\emph{Stage~4: Modularization.}
Trace and clutching on the open sector produce the full modular
Maurer--Cartan element $\Theta^{\mathrm{oc}} = \Theta_\cA
+ \sum \mu^{M_j}$.  The annulus trace
$\int_{S^1}\mathcal C \simeq \operatorname{HH}_\bullet(\mathcal C)$
is the first modular shadow of the open sector; clutching
along boundary circles via nodal degeneration raises genus.
\textsc{Annulus trace proved; full chain-level clutching is
programme.}

\medskip
Five negative principles constrain the architecture:
\begin{enumerate}[label=\textup{N\arabic*.},nosep]
\item \emph{Bar $\neq$ bulk.}
  The bar complex $\barB(A_b)$ is a factorization coalgebra
  classifying twisting morphisms.  The bulk
  $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\mathcal C)$ is the chiral
  derived center classifying bulk operators.  Different functors,
  different outputs.
\item \emph{Boundary algebra $=$ chart.}
  $A_b = \operatorname{End}_{\mathcal C}(b)$ depends on the choice
  of vacuum~$b$.  Only $\mathcal C$ itself and its derived center
  are intrinsic.
\item \emph{Tangential log geometry required.}
  The bordified curve $\widetilde{X}_D$ is a manifold with corners
  on an snc pair $(X,D)$.  Ordinary Fulton--MacPherson
  compactification is the $D = \varnothing$ special case.
\item \emph{Modularity $=$ trace $+$ clutching on the open sector.}
  The genus expansion is not an additional axiom on the closed
  algebra; it is determined by the cyclic trace on
  $\operatorname{End}_{\mathcal C}(b)$ and the gluing along
  boundary circles.
\item \emph{Honest scope.}
  The dg-shifted Yangian is proved for affine lineage (Kac--Moody
  and its standard reductions).  Extension to non-standard families
  is programme, not theorem.
\end{enumerate}

% ====================================================================
\section*{11.\quad Modular PVA quantization}
% ====================================================================

The open/closed world of Section~10 produces a genus-zero datum: the
Swiss-cheese MC element $\alpha_T$, the PVA
$(\mu,\{-_\lambda-\})$ on cohomology, and the KZ/BPZ shadow
connections at arity~$n$.  All of these are tree-level structures.
The question that forces the present section is: how does this
genus-zero structure extend across the genus filtration?  The
answer is the modular PVA quantization programme: a
genus-by-genus obstruction theory whose input is the genus-zero
PVA and whose output is the full modular MC element.  The
nonseparating degeneration operator $D_1$ is the primitive
genus-raising differential; it squares to zero, anticommutes
with the tree-level differential $D_0$, and defines a spectral
sequence whose obstructions are the quantization anomalies.

\subsection*{11.1.\enspace The one-edge principle}

To verify a modular operad structure, it suffices to check
compatibility with a single edge contraction: all higher-edge
relations follow from codimension-two cancellation.

If a complete filtered dg Lie algebra~$L$ carries a genus filtration
and its differential preserves genus exactly, then any genus-zero
Maurer--Cartan element
$\Theta_0\in\operatorname{MC}(\operatorname{gr}_F^0 L)$ extends
tautologically to a full MC element: genus by genus, the obstruction
class $[D_1\Theta_0]\in H^2(\operatorname{gr}^1 L)$ vanishes
because no differential raises genus.  Therefore every nontrivial
modular obstruction theory must contain a primitive genus-raising
operator.

The one-edge expansion of the stable-graph differential furnishes
this primitive.  Every one-edge degeneration of a stable graph is
either \emph{separating} (two vertices joined by one edge, total
genus preserved) or \emph{nonseparating} (one vertex acquiring one
loop, total genus raised by~$1$).  Set
\[
D_{\mathrm{exp}}\;=\;D_{\mathrm{sep}}+D_{\mathrm{nsep}},
\qquad
D_0\;:=\;D_{\mathrm{int}}+D_{\mathrm{sep}},
\qquad
D_1\;:=\;D_{\mathrm{nsep}}.
\]
Then $D_0$ preserves total genus, $D_1$ raises total genus by one,
and $(D_0+D_1)^2=0$ stratifies by genus shift into three identities:
\[
D_0^2=0,
\qquad
D_0 D_1+D_1 D_0=0,
\qquad
D_1^2=0.
\]
The first: $D_0$ is a differential.  The second: $D_1$ is a
$D_0$-derivation (it anticommutes with~$D_0$, so it descends to a
map on $D_0$-cohomology).  The third: $D_1$ squares to zero, so
the genus-one obstruction is a well-defined cohomology class.
The three identities are the codimension-two cancellation axiom
stratified by genus.

Trees govern chirality; loops govern
modularity.  $D_0$ (tree-level
degenerations) encodes OPE residues and
factorization.  $D_1$ (loop-creating
degenerations) encodes genus raising, trace
maps, the odd Laplacian.  The full modular bar theory is their
interaction.

\subsection*{11.2.\enspace The modular bar datum}

A \emph{modular bar datum} on a reduced, complete, finite-type
graded collection $F\mapsto C(F)$ consists of:
\begin{enumerate}[label=(\roman*)]
\item An internal differential $d\colon C(F)\to C(F)$ of
  degree~$+1$, with $d^2=0$.
\item For each one-edge expansion
  $\epsilon\in\operatorname{OE}(F)$ (an edge $e$ adjoined to the
  flag set~$F$, either separating (producing two flag sets
  $F_1\sqcup F_2=F\setminus\{f_1,f_2\}\sqcup\{f'_1,f'_2\}$)
  or nonseparating (the flag set $F$ acquires two new flags
  $\{h,h'\}$ identified as half-edges of~$e$, raising genus
  by~$1$)), a degree-$+1$ map
  \[
  \Delta_\epsilon\colon sC(F)
  \;\longrightarrow\;
  \orline(\epsilon)\otimes
  \bigotimes_{u\in V(\epsilon)}sC(\operatorname{Fl}_\epsilon(u)),
  \]
  where $\orline(\epsilon)$ is the orientation line of the
  new edge.
\item The \emph{codimension-two cancellation axiom}: for every
  connected stable graph with exactly two internal edges, the
  signed sum of the two ways of producing it by successive
  one-edge expansions is zero:
  \[
  \sum_{\substack{\epsilon_1,\epsilon_2\\
  \epsilon_1\circ\epsilon_2=\Gamma}}
  \operatorname{sgn}(\epsilon_1,\epsilon_2)\cdot
  \Delta_{\epsilon_2}\circ\Delta_{\epsilon_1}
  \;=\;0.
  \]
\item The anticommutation relation
  $d\circ\Delta_\epsilon+\Delta_\epsilon\circ d=0$.
\end{enumerate}
The total differential
$D=D_{\mathrm{int}}+D_{\mathrm{exp}}
=d+\sum_\epsilon\Delta_\epsilon$ satisfies $D^2=0$ by three
mechanisms: $d^2=0$ on vertex labels; anticommutation of~$d$
with one-edge expansions; and the codimension-two cancellation
axiom for two-edge graphs.  This is the algebraic incarnation
of the cell decomposition of $\overline{\cM}_{g,n}$ into
stable-graph strata: the codimension-two axiom is the statement
that every codimension-two stratum arises from two distinct
codimension-one degenerations, with opposite signs.

\subsection*{11.3.\enspace The complete modular bar coalgebra}

For a connected stable graph $\Gamma$ of genus~$g$ with
vertex set $V(\Gamma)$, edge set $E(\Gamma)$, and leg set
$L(\Gamma)$, set
\[
C[\Gamma]
\;:=\;
\orline(\Gamma)\otimes
\bigotimes_{v\in V(\Gamma)}sC(\operatorname{Fl}(v)),
\]
where $\orline(\Gamma)=\bigotimes_{e\in E(\Gamma)}\orline(e)$
is the total orientation line and $\operatorname{Fl}(v)$ is the
flag set at vertex~$v$.  The \emph{complete modular bar coalgebra}
is
\[
\mathrm B_{\mathrm{mod}}(C)
\;=\;
\prod_{[\Gamma]\in\mathsf{StGraph}^{\mathrm{conn}}}
\bigl(C[\Gamma]\bigr)_{\operatorname{Aut}(\Gamma)},
\]
completed over total genus
$g(\Gamma)=b_1(\Gamma)+\sum_{v}g(v)$.  The reduced coproduct is
edge contraction: contracting an internal edge of~$\Gamma$
strictly decreases the number of internal edges, so the
coalgebra is conilpotent.  The differential on
$\mathrm B_{\mathrm{mod}}(C)$ is the sum of the internal
differential (acting on vertex labels) and the expansion
differential (summing over all possible one-edge insertions into
each graph).

\subsection*{11.4.\enspace The strict modular deformation algebra}

The coderivation dg Lie algebra
\[
L_{\mathrm{mod}}(C)
\;:=\;
\operatorname{Coder}\bigl(\mathrm B_{\mathrm{mod}}(C)\bigr)[-1]
\]
is the \emph{strict modular deformation algebra}.  Its elements
are coderivations of the modular bar coalgebra, shifted by~$-1$
to place the Lie bracket in degree~$0$.  The convolution
description: the universal property of the cofree coalgebra gives
\[
L_{\mathrm{mod}}(C)
\;\cong\;
\operatorname{Hom}\bigl(\mathrm B_{\mathrm{mod}}(C),\,sC\bigr)[-1]
\]
with the commutator bracket
$[f,g]=f\star g-(-1)^{|f||g|}g\star f$, where
$f\star g$ is the convolution product (compose $f$ with the
coproduct, apply $g$ to one tensor factor, compose back).

The algebra $L_{\mathrm{mod}}(C)$ is complete filtered by genus:
$F^g L_{\mathrm{mod}}(C)$ consists of coderivations supported on
graphs of genus $\ge g$.  The completion is pro-nilpotent:
$F^1 L_{\mathrm{mod}}$ is a pro-nilpotent dg Lie algebra, and
$\operatorname{gr}^0 L_{\mathrm{mod}}$ is the tree-level
deformation algebra.  The full algebra is Lie-multiplicative:
the bracket $[f,g]$ respects the genus filtration, and the
associated graded inherits a dg Lie structure at each genus.

\subsection*{11.5.\enspace The genus-one obstruction theorem}

For a genus-zero MC element $\Theta_0\in\operatorname{MC}(\operatorname{gr}^0_F L)$
satisfying $D_0\Theta_0+\tfrac12[\Theta_0,\Theta_0]_0=0$,
the genus-one obstruction is
\[
\operatorname{Ob}_1(\Theta_0)
\;=\;
[D_1\Theta_0]
\;\in\;
H^2\!\bigl((\operatorname{gr}^1_F L)^{\Theta_0},\,d_0^{\Theta_0}\bigr),
\]
where $d_0^{\Theta_0}=D_0+[\Theta_0,-]$ is the $\Theta_0$-twisted
differential on the genus-one piece.  The class
$\operatorname{Ob}_1(\Theta_0)$ is well-defined:
$D_1\Theta_0$ is a $d_0^{\Theta_0}$-cocycle because of the
identity $D_0 D_1+D_1 D_0=0$ and the MC equation for~$\Theta_0$.
It vanishes if and only if $\Theta_0$ lifts to a genus-one MC
element $\Theta_0+\hbar\Theta_1$ satisfying
\[
(D_0+D_1)(\Theta_0+\hbar\Theta_1)
+\tfrac12[\Theta_0+\hbar\Theta_1,\Theta_0+\hbar\Theta_1]
\;=\;0
\qquad\bmod\;\hbar^2.
\]

In PVA coordinates, the nonseparating one-edge operator acts as
the reduced odd Laplacian.  For a cyclic $A_\infty$-algebra
$(A,m_k,\langle-,-\rangle)$ with basis $\{e^i\}$ and dual
basis $\{e_i\}$:
\[
\ell_1^{(1)}(a)
\;=\;
\hbar\Delta_{\mathrm{cyc}}(a)
\;:=\;
\hbar\sum_{i}m_2(e^i,m_2(a,e_i))
\;\in\;
A,
\]
the cyclic contraction over the single loop.  This is the
genus-raising operator: it takes a genus-$0$ vertex label and
produces a genus-$1$ correction by contracting one pair of
insertions through the cyclic pairing.  The full genus-one
obstruction $\operatorname{Ob}_1$ is the cohomology class of
$\Delta_{\mathrm{cyc}}(\Theta_0)$ in the twisted complex.

\subsection*{11.6.\enspace The $\mathcal W_3$ computation}

A \emph{filtered quadratic PVA} is a differential commutative
algebra freely generated by fields $u^1,\ldots,u^N$ and their
derivatives, with a $\lambda$-bracket encoded by a skew-adjoint
matrix differential operator
$\Pi^{ab}(\partial)=\sum_{m\ge 0}\Pi^{ab}_m\partial^m$ whose
coefficients have total generator degree at most~$2$.  Classical
$\mathcal W_3$ fits this pattern: two generators $T$
(weight~$2$) and $W$ (weight~$3$), with the quasi-primary
composite
\[
\Lambda\;=\;{:}TT{:}\;-\;\tfrac{3}{10}\,\partial^2 T
\]
controlling the nonlinear channel.  The $WW$~OPE is
\begin{align*}
W(z)W(w)
\;&\sim\;
\frac{c/3}{(z-w)^6}
\;+\;
\frac{2T}{(z-w)^4}
\;+\;
\frac{\partial T}{(z-w)^3}\\
&\quad\;+\;
\frac{1}{(z-w)^2}\biggl(\tfrac{3}{10}\partial^2 T
+\frac{16}{22+5c}\Lambda\biggr)
\;+\;
\frac{1}{z-w}\biggl(\cdots\biggr).
\end{align*}
At $c=-22/5$, the denominator $22+5c$ vanishes, $\Lambda$
becomes null, and $\mathcal W_3$ is no longer finitely generated
by $T$ and~$W$ alone.

The \emph{triangular $W$-normal form vanishing theorem} asserts:
in the local, translation-invariant, filtration-preserving sector,
$\operatorname{Ob}_1(\Theta_0)=0$ for classical $\mathcal W_3$.
The computation: the relevant cohomology group is
\[
H^1\!\bigl((\operatorname{gr}^1 L)^{\Theta_0},\,d_0^{\Theta_0}\bigr)
\;\cong\;\mathbb C\cdot\partial_c P_c\,,
\]
one-dimensional, spanned by the central-parameter
direction~$\partial_c P_c$, where $P_c$ is the $\lambda$-bracket
matrix viewed as a function of~$c$.  Concretely: every genus-one
lift of the classical $\mathcal W_3$ PVA is gauge equivalent to a
renormalization of the central charge $c\mapsto c+\hbar c_1$.
The genus-one quantum $\mathcal W_3$ algebra is the unique quantization
in the direction~$\partial_c$.

\subsection*{11.7.\enspace Curved extension via $S$-tails}

In the inhomogeneous quadratic setting (Gui--Li--Zeng), the correct
input is a \emph{twisted pair} $(B,B^\circ,S)$: a CDG-algebra~$B$,
a CDG-coalgebra~$B^\circ$, and a curvature element~$S$.
An \emph{$S$-tail expansion} attaches a new univalent
$S$-decorated vertex to a pre-existing corolla: formally, a
unary expansion map
\[
\Delta_S\colon sC(F)\;\longrightarrow\;sC(F\sqcup\{\bullet,\star\})
\]
followed by contraction of the new internal edge, with the
vertex~$\star$ carrying the curvature label~$S$.  Adjoining
$S$-tail expansions to the one-edge expansion set, with the
same codimension-two compatibilities, produces a \emph{curved
complete modular bar object}.

The Maurer--Cartan equation in the curved setting is:
\[
\mu\!\bigl((S+\alpha)\boxtimes(S+\alpha)\bigr)\;=\;0,
\]
the modular extension of the Gui--Li--Zeng curved equation.
The element $S+\alpha$ combines the curvature~$S$ (a genus-zero
scalar, the analogue of $m_0$) with the deformation
parameter~$\alpha$.  The equation unpacks genus by genus: at
genus~$0$, it is the curved $A_\infty$ MC equation
$\sum_k m_k(\alpha^{\otimes k})=0$ with $m_0=S$; at genus~$1$,
it is $\Delta_{\mathrm{cyc}}(S+\alpha)=0$, the vanishing of the
curved odd Laplacian; at genus~$g$, it is the BV quantum master
equation $\hbar\Delta(e^{(S+\alpha)/\hbar})=0$.

\subsection*{11.8.\enspace Genus-zero comparison with Gui--Li--Zeng}

At tree level, the modular MC equation reduces to the
classical twisting morphism equation.  For a Koszul pair
$(\cA,\cA^!)$ with $\cA^!$ a CDG algebra with curvature~$S$,
the genus-zero MC space is
\[
\operatorname{MC}_0(L_{\mathrm{mod}})
\;\cong\;
\operatorname{Hom}_{\mathsf{dg}}(\cA,B^\circ)
\;\hookrightarrow\;
\operatorname{MC}(\cA^!\widehat{\otimes}\cB),
\]
where $\cB$ is a test algebra.  This recovers the Gui--Li--Zeng
correspondence: tree-level MC elements of the modular deformation
algebra are twisting morphisms $\cA\to B^\circ$, which are in
bijection with CDG-algebra morphisms $B\to\cA^!\widehat\otimes\cB$.
The modular theory is the genus extension of this classical picture.


% ====================================================================
\section*{12.\quad Holographic modular Koszul duality}
% ====================================================================

The open/closed world (Section~10) supplies the three-dimensional
geometric framework; the modular PVA quantization programme
(Section~11) supplies the genus-by-genus obstruction theory.  The
holographic modular Koszul datum packages both into a single
algebraic object: a six-component structure that records the
boundary algebra, its Koszul dual, the line-operator category, the
spectral $R$-matrix, the universal MC element, and the modular
shadow connection.  Every ingredient constructed so far (the
bar complex, the shadow obstruction tower, the Swiss-cheese structure, the PVA
descent, the genus expansion) appears as a projection of this
datum.  The datum is not a summary; it is the natural unit of
holographic data, the smallest package from which the full
correspondence can be reconstructed.

\subsection*{12.1.\enspace The holographic modular Koszul datum}

Every three-dimensional holomorphic-topological system~$T$ is
controlled by a \emph{holographic modular Koszul datum}
\[
\mathcal H(T)
\;=\;
\bigl(\cA,\;\cA^!,\;\cC,\;r(z),\;\Theta_\cA,\;\nabla^{\mathrm{hol}}\bigr),
\]
defined as follows.
\begin{enumerate}[label=(\roman*)]
\item $\cA$: the \emph{boundary chiral algebra}, a chiral algebra
  on a complex curve $X$.  It is the algebra of boundary local
  operators of~$T$ restricted to the holomorphic boundary
  $\{0\}\times X\subset\mathbb R_+\times X$.
\item $\cA^!$: the \emph{strict chiral Koszul dual} of~$\cA$, obtained by
  linear duality of bar cohomology:
  $\cA^!=(\cA^{\mathrm i})^\vee$ where
  $\cA^{\mathrm i}=H^*(\barB(\cA))$.  In the holographic setting,
  $\cA^!$ is a \emph{dg-shifted Yangian}.  The bar complex
  $\barB(A_b)$ is an algebra over the two-coloured
  Swiss-cheese operad $\SCchtop$: chiral on the closed colour,
  $E_1$ on the open colour.  The Koszul dual $\cA^!$ is the
  $E_1$-projection of the $\SCchtop$-dual; it carries an
  $E_1$-algebra structure from the topological direction.
\item $\cC\simeq\cA^!\text{-}\mathsf{mod}$: the \emph{line-operator
  category}, a braided tensor category.  Objects are line defects
  of~$T$ (topological lines in $\mathbb R_+$); morphisms are
  junction operators; the braiding comes from crossing in the
  holomorphic plane.
\item $r(z)\in\cA^!\otimes\cA^!((\!( z^{-1})\!))$: the
  \emph{dg-shifted Yangian $R$-matrix}, a meromorphic endomorphism
  with a pole at $z=0$.  It satisfies the classical Yang--Baxter
  equation
  \[
  [r_{12}(z_1{-}z_2),\,r_{13}(z_1{-}z_3)]
  +[r_{12}(z_1{-}z_2),\,r_{23}(z_2{-}z_3)]
  +[r_{13}(z_1{-}z_3),\,r_{23}(z_2{-}z_3)]
  \;=\;0.
  \]
  The $R$-matrix is the binary genus-$0$ shadow of~$\Theta_\cA$:
  \[
  r(z)\;=\;\operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA).
  \]
\item $\Theta_\cA\in\operatorname{MC}(\mathfrak g^{\mathrm{mod}}_\cA)$:
  the \emph{universal Maurer--Cartan element} of the modular
  convolution $L_\infty$-algebra, existing unconditionally by the
  bar-intrinsic construction $\Theta_\cA:=D_\cA-d_0$.  All lower
  structures ($\kappa$, $r(z)$, the shadow connection) are
  projections of $\Theta_\cA$ to specific genus and arity components.
\item $\nabla^{\mathrm{hol}}_{g,n}=d-\operatorname{Sh}_{g,n}(\Theta_\cA)$:
  the \emph{modular shadow connection}, a connection on the modular
  shadow bundle over $\overline{\cM}_{g,n}$.  Flatness of
  $\nabla^{\mathrm{hol}}$:
  \[
  (\nabla^{\mathrm{hol}}_{g,n})^2
  \;=\;
  d\operatorname{Sh}_{g,n}(\Theta_\cA)
  +\tfrac12[\operatorname{Sh}_{g,n}(\Theta_\cA),
  \operatorname{Sh}_{g,n}(\Theta_\cA)]
  \;=\;0
  \]
  is the MC equation projected to genus~$g$ and arity~$n$.
\end{enumerate}

\subsection*{12.2.\enspace The collision filtration}

The modular convolution algebra $\mathfrak g^{\mathrm{mod}}_\cA$
carries a \emph{collision filtration}
$F^0_{\mathrm{coll}}\supset F^1_{\mathrm{coll}}\supset\cdots$
indexed by the minimum pairwise distance on
$\operatorname{FM}_n(\mathbb C)$: depth~$0$ is the
free-propagation regime (all points well-separated), depth~$1$ is
the first collision stratum (one pairwise collision), depth~$k$
is the $k$-fold nested collision locus (a sequence of $k$ nested
screens in the FM compactification).

The associated spectral sequence has
\[
E_1^{p,*}
\;=\;
H^*\!\bigl(\operatorname{gr}_{\mathrm{coll}}^p\,
\mathfrak g^{\mathrm{mod}}_\cA,\;d_0\bigr),
\]
with $E_1^{0,*}$ the free-field contribution (no collisions,
$d_0$ the free differential) and $E_1^{1,*}$ the collision
residues (single pairwise collisions, extracting the leading
OPE singularity).  The first differentials $d_1\colon
E_1^{p,*}\to E_1^{p+1,*}$ are Arnold-type cancellations: the
Arnold relation on $\operatorname{FM}_3(\mathbb C)$ forces
$d_1^2=0$ on the $E_1$~page.  The spectral sequence converges
to $H^*(\mathfrak g^{\mathrm{mod}}_\cA)$, with the collapse at
the $E_r$~page governed by the shadow depth: for
class-$\mathbf{G}$ algebras (depth~$2$), the spectral sequence
collapses at $E_2$; for class-$\mathbf{M}$ algebras
(depth~$\infty$), it does not collapse at any finite page.

\subsection*{12.3.\enspace Four proved recovery theorems}

The collision filtration recovers four structures from $\Theta_\cA$.

\medskip
\noindent\emph{(R1) Collision residue = twisting.}
The depth-$1$ collision stratum at arity~$2$ extracts the binary
shadow:
\[
\operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)
\;=\;\pi_\cA,
\]
the universal twisting morphism producing the
dg-shifted Yangian $r_\cA(z)$.  The collision
residue extracts the leading OPE pole
$a_{(0)}b/(z_1-z_2)$; the MC equation at this depth is the
twisting morphism equation
$\partial\pi+\pi\star\pi=0$.

\medskip
\noindent\emph{(R2) CYBE from Arnold.}
The three boundary divisors of $\overline M_{0,4}$ correspond
to the three channels $(12|34)$, $(13|24)$, $(14|23)$.  Evaluating
the Arnold relation $\eta_{12}\wedge\eta_{23}+\eta_{23}\wedge\eta_{31}
+\eta_{31}\wedge\eta_{12}=0$ on the Casimir tensor
$\Omega\otimes\Omega\in(\cA^!)^{\otimes 3}$ produces the three
terms of the CYBE:
\[
[r_{12}(z_{12}),\,r_{13}(z_{13})]
\;+\;
[r_{12}(z_{12}),\,r_{23}(z_{23})]
\;+\;
[r_{13}(z_{13}),\,r_{23}(z_{23})]
\;=\;0,
\]
where $z_{ij}=z_i-z_j$.  Each bracket corresponds to a boundary
divisor, and the Arnold relation is the vanishing of the boundary
integral.

\medskip
\noindent\emph{(R3) Affine shadow/KZ comparison on the affine comparison surface.}
For the affine algebra $\cA=\widehat{\fg}_k$, on the affine
Kac--Moody comparison surface the genus-$0$
shadow one-form at arity~$n$ is the Knizhnik--Zamolodchikov connection
form:
\[
\operatorname{Sh}_{0,n}(\Theta_{\widehat{\fg}_k})
\;=\;
\sum_{i<j}r_{ij}(z_i{-}z_j)\,d\log(z_i{-}z_j)
\;=\;
\frac{1}{h^\vee+k}\sum_{i<j}\frac{\Omega_{ij}\,dz_{ij}}{z_{ij}}\,,
\]
where $r_{ij}$ denotes the propagator-weighted Casimir
$\Omega_{ij}/(h^\vee{+}k)$, not the spectral $r$-matrix.
Flatness of $\nabla_{\mathrm{KZ}}=d-\operatorname{Sh}_{0,n}$
is the MC equation at genus~$0$ and arity~$n$.  For
$\cA=\operatorname{Vir}_c$, on the Virasoro degenerate-module
comparison surface the analogous Virasoro conformal Ward extraction,
together with higher collision residues, yields the
BPZ differential equations.  The affine Drinfeld--Kohno theorem
compares the braid-group monodromy of the genus-$0$ shadow of
$\Theta_{\widehat{\fg}_k}$ with the corresponding quantum-group
representation category.

\medskip
\noindent\emph{(R4) Quartic = $L_\infty$ obstruction.}
The quartic resonance class
\[
[\mathfrak R^{\mathrm{mod}}_4(\cA)]
\;=\;
[o_4(\cA)]
\;\in\;
H^2\!\bigl(\cA^{\mathrm{sh}}_{4,0}\bigr)
\]
is the obstruction to extending the Yangian seed $r(z)$ from
arity~$2$ to arity~$4$.  It
vanishes for classes $\mathbf{G}$, $\mathbf{L}$,
$\mathbf{C}$ (the $R$-matrix
extends to all arities) and is nonzero for class~$\mathbf{M}$
(the nonlinear OPE forces a genuine
quartic obstruction:
$Q^{\mathrm{contact}}_{\operatorname{Vir}}=10/[c(5c+22)]$).

\subsection*{12.4.\enspace Five conjectural theorem targets}

\begin{enumerate}[label=(\roman*)]
\item \emph{Boundary-defect realization.}
  The boundary chiral algebra $\cA_\partial(T)$ and its Koszul
  dual $\cA^!_\partial(T)$ are the two algebras appearing in the
  holographic datum for every 3d HT system~$T$, with
  $\cC\simeq\cA^!\text{-mod}$ as braided tensor category of line
  operators.  The physical content: boundary local operators and
  bulk-to-boundary maps determine the full holographic datum up
  to quasi-isomorphism.

\item \emph{Yangian-shadow.}
  In full derived generality: for every HT system~$T$, the
  collision residue
  $\operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$ recovers
  the dg-shifted Yangian $r(z)$ attached to~$T$, not merely at
  the classical level but at the chain level, including all
  higher homotopies of the $A_\infty$ structure.

\item \emph{Sphere reconstruction.}
  The Gaiotto--Zhang (2026) commuting differentials on the
  non-planar sphere algebra are the scalar shadow
  $\operatorname{Sh}_{0,n}(\Theta_\cA)$: the 2026 sphere algebra
  is the binary genus-$0$ shadow of the modular MC class.  The
  $n$-point sphere amplitude
  $\langle\cO_1(z_1)\cdots\cO_n(z_n)\rangle_{S^2}$ is, on the
  established genus-$0$ comparison surfaces, a flat section of
  $\nabla^{\mathrm{hol}}_{0,n}$.

\item \emph{Quartic resonance obstruction.}
  The quartic resonance class $\mathfrak R^{\mathrm{mod}}_4$, the
  first global nonlinear invariant, is
  the first test of the modular datum beyond the spectral
  determinant: its non-vanishing for class-$\mathbf{M}$ algebras
  is the quantitative obstruction to planarity of the holographic
  system, measuring the failure of the large-$N$ expansion to
  truncate at tree level.

\item \emph{Singular-fiber descent.}
  At degenerate complex structure (boundary of
  $\overline{\cM}_{g,n}$), the modular datum degenerates to the
  boundary of the Mok compactification:
  $\nabla^{\mathrm{hol}}|_{\partial\overline{\cM}}\sim
  \nabla^{\mathrm{clutch}}$ with residues controlled by the
  clutching law of~$\Theta_\cA$.  The clutching law:
  $\Theta_\cA|_{\sigma_\Gamma}=\prod_{v\in V(\Gamma)}\Theta_v
  \cdot\prod_{e\in E(\Gamma)}P_e$, where $\sigma_\Gamma$
  is a boundary stratum of $\overline{\cM}_{g,n}$ labelled by
  a stable graph~$\Gamma$, $\Theta_v$ is the vertex MC element,
  and $P_e$ is the edge propagator.
\end{enumerate}

\subsection*{12.5.\enspace The colored modular deformation object}

A holomorphic-topological theory~$T$ produces three observation
algebras:
\[
\mathrm{Obs}^{\mathrm{hol}}\;(\text{bulk}),
\qquad
\mathrm{Obs}^\partial\;(\text{boundary}),
\qquad
\mathrm{Obs}^\ell\;(\text{line}).
\]
The colored Swiss-cheese FM space
$\operatorname{FM}^{\log}_{\bullet,\mathrm{SC}}$ encodes the
collision geometry of all three simultaneously: bulk points in
$\mathbb C$, boundary points on $\mathbb R\subset\mathbb C$, and
line points on individual copies of $\mathbb R_+$.  The
three-color modular deformation object is
\[
\mathfrak g^{\mathrm{HT,log}}_{\mathrm{mod}}
\;=\;
\operatorname{hom}^{\alpha_{\mathrm{HT}}}\!\bigl(
C_\bullet(\operatorname{FM}^{\log}_{\bullet,\mathrm{SC}}),\;
\operatorname{End}_{\mathrm{Ch}_\infty}(
\mathrm{Obs}^{\mathrm{hol}}_\infty,\,
\mathrm{Obs}^\partial_\infty,\,
\mathrm{Obs}^\ell_\infty)
\bigr),
\]
the convolution $sL_\infty$-algebra between the chains on the
colored log-FM space and the endomorphism operad of the three
observation algebras.  The three colors interact through the
Swiss-cheese operadic structure: bulk fields propagate to the
boundary (closed-to-open maps), boundary fields propagate to
lines (open-to-open composition), and lines cannot produce bulk
fields (the $\varnothing$-prohibition of $\mathsf{SC}$).

The modular effective action is the graph-sum
\[
S^{\mathrm{mod}}_{\mathrm{HT}}
\;=\;
\sum_{\Gamma\in\mathsf{StGraph}_{\mathrm{SC}}}
\frac{\hbar^{b_1(\Gamma)}}{|\operatorname{Aut}(\Gamma)|}
\,W^{\log}_\Gamma\,O_\Gamma\,,
\]
where the sum is over connected stable graphs $\Gamma$ decorated by
the three colors, $b_1(\Gamma)$ is the first Betti number,
$W^{\log}_\Gamma$ is the Feynman weight (a period integral on the
log-FM stratum $\sigma_\Gamma$), and $O_\Gamma$ is the vertex
operator (the tensor product of observation-algebra elements at
each vertex).  The BV quantum master equation
\[
\bigl(d_{\mathrm{BV}}+\hbar\Delta_{\mathrm{odd}}\bigr)
\exp\!\bigl(S^{\mathrm{mod}}_{\mathrm{HT}}/\hbar\bigr)
\;=\;0
\]
is the single equation governing the 3d HT system~$T$.  At
genus~$0$ ($\hbar^0$): the classical BV master equation
$\{S_0,S_0\}=0$.  At genus~$1$ ($\hbar^1$): the one-loop anomaly
cancellation $\Delta_{\mathrm{odd}}S_0+\{S_0,S_1\}=0$.  At
genus~$g$ ($\hbar^g$): the $g$-loop Ward identity.

\subsection*{12.6.\enspace The Khan--Zeng bridge}

Khan and Zeng construct a three-dimensional holomorphic-topological
Poisson sigma model on the half-space
$\mathbb R_+\times\mathbb C$ attached to a freely generated PVA.
The field content: a $\fg$-valued $(0,1)$-form $A_{\bar z}$
on~$\mathbb C$, a $\fg^*$-valued scalar $\phi$, and a
$\fg$-valued $1$-form $\eta$ along~$\mathbb R_+$.  The action is
\[
S_{\mathrm{KZ}}
\;=\;
\int_{\mathbb R_+\times\mathbb C}
\bigl(\langle\phi,\,\bar\partial A\rangle
+\langle\phi,\,\tfrac12\{A_\lambda A\}|_{\lambda=0}\rangle
+\langle\eta,\,d_t\phi\rangle\bigr)\,
dt\wedge dz\wedge d\bar z.
\]
The results:
\begin{enumerate}[label=(\roman*)]
\item Gauge invariance of $S_{\mathrm{KZ}}$ holds if and only if
  the $\lambda$-bracket $\{-_\lambda-\}$ satisfies the PVA Jacobi
  identity.  The gauge algebra is the Lie conformal algebra
  underlying the PVA.
\item A Virasoro element $T$ in the PVA upgrades the symmetry:
  the stress tensor provides a coupling to worldsheet gravity,
  promoting holomorphic-topological to fully topological
  (diffeomorphism-invariant on the boundary $\{0\}\times\mathbb C$).
\item The boundary theory on $\{0\}\times\mathbb C$ carries a
  $(-1)$-shifted Poisson bracket $\{-,-\}_{-1}$ and produces the
  genus-zero quantization problem: deforming $\{-,-\}_{-1}$ to
  a differential $Q=Q_0+\hbar Q_1+\cdots$ with $Q^2=0$.
\item The modular extension, coupling the bulk theory to stable
  curves at genus $g\ge 1$ via the fibration
  $\cC_g\to\overline{\cM}_g$, controls the full genus tower of
  the quantum Koszul datum.
\end{enumerate}
The deformation-quantization pipeline:
\[
\text{classical coisson shadow}
\;\xrightarrow{\;\text{KZ quantization}\;}\;
\text{genus-$0$ quantum Koszul}
\;\xrightarrow{\;\text{modular lift}\;}\;
\mathcal H(T).
\]
The first arrow is perturbative quantization of the Khan--Zeng
action on $\mathbb P^1$ (tree-level Feynman diagrams).  The
second arrow is the genus-by-genus obstruction theory of
\S\S10--11, extending the genus-$0$ MC element across the genus
filtration.

The bridge is completed in Volume~II by the \emph{doubling
theorem}: the half-space BV problem for any logarithmic
$\mathsf{SC}^{\mathrm{ch,top}}$-algebra embeds into the doubled
whole-space via the method of images, and the reflected weight
identity, the condition for the boundary algebra to be a vertex
algebra, is the $\sigma$-invariant restriction of the standard
Stokes identity on the doubled Fulton--MacPherson compactification.
The affine Poisson--vertex sigma model satisfies the hypotheses of
the physics bridge theorem (BV data, one-loop finiteness, polynomial
interactions), so it is a logarithmic
$\mathsf{SC}^{\mathrm{ch,top}}$-algebra; Drinfeld--Sokolov
reduction preserves this structure.  The entire standard
landscape (Kac--Moody, Virasoro, $\mathcal W_N$) enters through
these two gates.  The six-component holographic datum
\[
\bigl(B_\partial,\;B_\partial^!,\;\cC_{\mathrm{line}},\;r(z),\;
\Theta_{B_\partial},\;\nabla^{\mathrm{hol}}\bigr)
\]
exists and is consistent for every logarithmic
$\mathsf{SC}^{\mathrm{ch,top}}$-algebra: bulk $\simeq$ derived center
of boundary, line operators $\simeq$ Koszul-dual modules, spectral
$R$-matrix from the Laplace-transformed $\lambda$-bracket.

The genus expansion of the modular bar differential,
$D = \sum_{g \ge 0}\hbar^g D^{(g)}$ with
$D^{(g)} = \sum_{\Gamma:\,g(\Gamma)=g}|\Aut(\Gamma)|^{-1}D_\Gamma$,
is the Feynman transform of the modular operad; the canonical MC
element $\delta_\cA = D - D^{(0)}$ computes the positive-genus
corrections.  The combinatorial structure (stable graphs,
automorphism weights, genus bookkeeping) is the mathematical shadow
of the 't~Hooft expansion.  The identification $\hbar
\leftrightarrow 1/N$ for a specific holographic model remains the
principal open bridge from the algebraic machine to gauge-theory
holography.

\subsection*{12.7.\enspace The Heisenberg holographic datum}

The base case: shadow class~$\mathbf G$, depth~$2$, trivial line-operator
category, scalar $R$-matrix.
For $\cA=\mathcal H_k$:
\begin{align*}
\cA&=\mathcal H_k,
&\cA^!&=\mathrm{Sym}^{\mathrm{ch}}(V^*),
&\cC&=\mathsf{Vect},\\[4pt]
r(z)&=k/z,
&R(z)&=\exp(k/z),
&\Theta_{\mathcal H_k}&=k\cdot\eta\otimes\Lambda.
\end{align*}
The shadow connection is trivial:
$\nabla^{\mathrm{hol}}_{g,n}=d$ for all $(g,n)$, because the MC
element is scalar (it lives in the one-dimensional space
$\mathbb C\cdot\eta\otimes\Lambda$, and the shadow
$\operatorname{Sh}_{g,n}(\Theta_{\mathcal H_k})$ is a scalar
multiple of the identity, producing a trivial connection).

All five conjectural targets are trivially verified:
\begin{enumerate}[label=(\roman*),nosep]
\item The boundary algebra $\mathcal H_k$ is free
  (one generator, no nonlinear OPE).
\item The Koszul dual $\mathrm{Sym}^{\mathrm{ch}}(V^*)$
  is the curved symmetric chiral algebra with curvature
  $m_0 = -k\omega$
  (Theorem~\ref{thm:frame-heisenberg-koszul-dual};
  note: $\cH_k^! \neq \cH_{-k}$).
\item The line-operator category is $\mathsf{Vect}$: no
  nontrivial lines (the $R$-matrix is scalar, so the braiding
  is symmetric, and $\cH_k^!$-modules over $\mathsf{Vect}$
  are just vector spaces).
\item The quartic obstruction vanishes: shadow class~$\mathbf{G}$,
  $o_4(\mathcal H_k)=0$.
\item Singular-fiber descent is trivial: $\Theta_{\mathcal H_k}$
  has no dependence on moduli.
\end{enumerate}


\subsection*{12.8.\enspace The affine $\widehat{\mathfrak{sl}}_2$ holographic datum}

The first nontrivial
holographic example: class~$\mathbf L$,
depth~$3$, $r(z)=\Omega/z$ (Yang's solution of the CYBE), line-operator category $Y(\mathfrak{sl}_2)\text{-mod}$.
The braiding is nonsymmetric, the shadow connection is KZ,
and quantum-group representation theory emerges from
genus-$0$ monodromy.

The Koszul dual is
$\widehat{\mathfrak{sl}}_2{}_{-k-4}$ (Feigin--Frenkel involution).  The holographic datum is 3d Chern--Simons at level~$k$;
Drinfeld--Kohno (KZ monodromy = quantum-group braiding) follows from the genus-$0$ shadow
connection.

The datum ($3$d Chern--Simons at level~$k$):
\[
\mathcal H(\widehat{\mathfrak{sl}}_2{}_k)
\;=\;
\Bigl(
\widehat{\mathfrak{sl}}_2{}_k,\;
\widehat{\mathfrak{sl}}_2{}_{-k-4},\;
\mathcal O_q^{\mathrm{sh}},\;
\frac{\Omega}{z},\;
\Theta_k,\;
d-\kappa_k\,\omega_g
\Bigr),
\]
$r(z)=\Omega/z$ (Casimir), $q=e^{i\pi/(k+2)}$,
$\kappa_k=3(k+2)/4$.
At $k=-2$: $\kappa=0$ (uncurved), the center
$\mathfrak z(\widehat{\mathfrak g}_{-h^\vee})$ is the
Feigin--Frenkel algebra of $\mathfrak{sl}_2$-opers.
The monodromy of the KZ connection
$\nabla_{\mathrm{KZ}} = d - \hbar\,\Omega/z$
(with $\hbar = 1/(k{+}2)$)
is compared with the quantum-group $R$-matrix of
$U_q(\mathfrak{sl}_2)$ by the affine Drinfeld--Kohno package;
on the reduced evaluation comparison surface,
$\cC_{\mathrm{line}}^{\mathrm{red}}|_{\mathrm{eval}}$ is
identified with the corresponding quantum-group side
(Volume~II), and the colored Jones
polynomial is recovered from the monodromy representation classified by the bar complex, the Steinberg convolution of the chiral
self-intersection on $\operatorname{FM}_k(\mathbb C)$.

\subsection*{12.9.\enspace The Virasoro holographic datum}

The Virasoro algebra is the first example of shadow
class~$\mathbf M$ (mixed, infinite depth): the $R$-matrix
$r_c(z) = (c/2)/z^3 + 2T/z$ has both a third-order pole
(gravitational) and a first-order pole (stress-tensor exchange),
and the quartic contact invariant
$Q^{\mathrm{contact}} = 10/[c(5c+22)]$ is nonzero.  The
holographic datum packages three-dimensional quantum gravity on the
half-space $\mathbb R_+ \times \mathbb C$: the Koszul dual is
$\mathrm{Vir}_{26-c}$ (self-dual at $c=13$, not $c=26$), the
shadow connection carries curvature proportional to
$\kappa_c = c/2$, and the transferred coproduct is strictly
primitive at all arities: gravity does not produce particles,
only braids them.

\medskip\noindent
\emph{Virasoro at central charge~$c$}
($3$d gravity on $\mathbb R_+\times\mathbb C$):
\begin{align*}
\mathcal H(\mathrm{Vir}_c)
&\;=\;
\Bigl(
\mathrm{Vir}_c,\;
\mathrm{Vir}_{26-c},\;
\cC_c,\;
r_c(z),\;
\Theta_c,\;
\nabla^{\mathrm{hol}}_c
\Bigr),\\[6pt]
r_c(z)
&\;=\;
\frac{c/2}{z^3}+\frac{2T}{z}\,,
\qquad
\kappa_c\;=\;\frac{c}{2}\,,\\[4pt]
\nabla^{\mathrm{hol}}_{1,1}
&\;=\;
d-\kappa_c\,\omega_1
-\frac{10}{c(5c+22)}\,\delta_4
-\cdots\,.
\end{align*}
The shadow connection has curvature $\kappa_c\,\omega_g$
at leading order.  The quartic contact correction
$\mathfrak Q=10/[c(5c+22)]$ is the first term sensitive to
the planted-forest boundary of $\overline{\cM}_{g,n}$.
The genus tower has the formal structure of a
perturbative expansion of $3$d quantum gravity.
The transferred coproduct $\Delta_z^{\mathrm{Vir}}$ is strictly
primitive at all arities
(Principle~\ref{princ:gravitational-primitivity}): the
ghost-number obstruction intrinsic to DS reduction kills every
HPL tree correction.  All gravitational dynamics resides in
the collision residue $r_c(z) = (c/2)/z^3 + 2T/z$ and the
infinite $\Ainf$ product tower; the coproduct channel is
identically zero.  Gravity does not produce particles, only
braids them.

\subsection*{12.10.\enspace The M2 brane example}

The first genuinely interacting holographic
example: boundary algebra $\mathcal W_{1+\infty}$
(infinitely many generators), Koszul dual a dg-shifted
Yangian for $\mathfrak{psl}(2|2)$,
line-operator category a quantum affine superalgebra.  All three
genus-$2$ shells are active, with the
planted-forest shell receiving its
first nontrivial contribution from Mok's log-FM strata.

The system arises from
3d $\cN=4$ ADHM gauge theory: $N$ M2 branes probing
$\mathbb C^2/\mathbb Z_k$.

\medskip
\noindent\textbf{The boundary algebra.}
The boundary chiral algebra $\cA_{M2,N}$ at finite~$N$ is the VOA
of the 3d $\cN=4$ theory on $\mathbb R_+\times\mathbb C$.  At
large~$N$, the boundary VOA $\cA_{M2,\infty}$ is a $\mathcal W$-algebra
of type $\mathcal W_{1+\infty}[c]$ at $c\sim N$: it has infinitely
many strong generators of weights $1,2,3,\dots$, with OPE
coefficients that are rational functions of~$N$.

The OPE structure contains both simple and higher poles.  The
stress tensor $T$ (weight~$2$) has the Virasoro OPE with
$c=c(N)$; the weight-$3$ primary~$W$ has a nonlinear $WW$ OPE
involving the quasi-primary $\Lambda={:}TT{:}-\frac{3}{10}\partial^2T$
at order $(z-w)^{-2}$; and the weight-$s$ generators for $s\ge 4$
produce nested composites that make the shadow obstruction tower infinite.

\medskip
\noindent\textbf{The Koszul dual.}
The chiral Koszul dual $\cA^!_{M2,\infty}$ is a dg-shifted Yangian
for the Lie superalgebra $\mathfrak{psl}(2|2)$:
\[
\cA^!_{M2,\infty}
\;\simeq\;
Y^{\mathrm{dg}}_{\hbar}(\mathfrak{psl}(2|2)).
\]
The $R$-matrix
$R_{M2}(z)\in Y^{\mathrm{dg}}_\hbar(\mathfrak{psl}(2|2))
\otimes Y^{\mathrm{dg}}_\hbar(\mathfrak{psl}(2|2))[[z^{-1}]]$
is the collision residue
$R_{M2}(z)=\operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_{M2})$.
The classical $r$-matrix $r_{M2}(z)=\Omega_{\mathfrak{psl}(2|2)}/z$
satisfies the classical Yang--Baxter equation, which is the Arnold
relation on $\operatorname{FM}_3(\mathbb C)$ evaluated on the
$\mathfrak{psl}(2|2)$-Casimir.

\medskip
\noindent\textbf{The line-operator category.}
\[
\cC_{M2}
\;\simeq\;
\operatorname{Rep}\!\bigl(
U_q(\widehat{\mathfrak{psl}}(2|2))
\bigr),
\]
where $q=e^{2\pi i/(k+2)}$.  The line operators are modules for the
quantum affine superalgebra.  The spectral braiding
$R_{M2}(z)\colon L_1\otimes L_2\xrightarrow{\sim}L_2\otimes L_1$
on pairs of line operators satisfies the Yang--Baxter equation:
Stokes' theorem on $\operatorname{FM}_3(\mathbb C)$ decomposes
the boundary into three collision divisors, one for each crossing
in the YBE.

\medskip
\noindent\textbf{The holographic datum.}
The full six-component holographic modular Koszul datum is:
\begin{align*}
\cA &= \cA_{M2,\infty}\;(\text{boundary }\mathcal W_{1+\infty}),
&\cA^! &= Y^{\mathrm{dg}}_\hbar(\mathfrak{psl}(2|2)),\\[3pt]
\cC &= \operatorname{Rep}(U_q(\widehat{\mathfrak{psl}}(2|2))),
&r(z) &= \Omega_{\mathfrak{psl}(2|2)}/z,\\[3pt]
\Theta_{M2} &= \sum_\Gamma
  \frac{W^{\log\mathrm{FM}}_\Gamma}{|\operatorname{Aut}(\Gamma)|}
  \otimes\Phi^{M2}_\Gamma,
&\nabla^{\mathrm{hol}}_{g,n} &= d-\operatorname{Sh}_{g,n}(\Theta_{M2}).
\end{align*}

\medskip
\noindent\textbf{Shadow obstruction tower analysis.}
The MC element $\Theta_{M2}$ has infinite shadow depth
(class~$\mathbf M$: mixed modular):
\begin{itemize}[nosep]
\item The cubic shadow $\mathfrak C_{M2}\neq 0$ because
  $\cA_{M2,\infty}$ has a nonabelian current subalgebra.
\item The quartic contact shadow
  $Q^{\mathrm{contact}}_{M2}\neq 0$ because
  ${:}TT{:}-\frac{3}{10}\partial^2 T$ appears in the $WW$~OPE
  with coefficient $16/(22+5c(N))$.
\item The quintic obstruction
  $o^{(5)}_{M2}=\{\mathfrak C_{M2},Q^{\mathrm{contact}}_{M2}\}_H
  \neq 0$: the tower is infinite.
\end{itemize}
At genus~$2$, all three shells contribute:
$\Theta^{(2)}_{\mathrm{loop}\circ\mathrm{loop}}\neq 0$,
$\Theta^{(2)}_{\mathrm{sep}\circ\mathrm{loop}}\neq 0$,
$\Theta^{(2)}_{\mathrm{pf}}\neq 0$.  The planted-forest shell
$\Theta^{(2)}_{\mathrm{pf}}$ is the first contribution from Mok's
log-FM strata to the holographic genus expansion.

\medskip
\noindent\textbf{The modular shadow connection.}
The shadow connection
$\nabla^{\mathrm{hol}}_{g,n}=d-\operatorname{Sh}_{g,n}(\Theta_{M2})$
is nontrivial: the shadow $\operatorname{Sh}_{g,n}$ is a
matrix-valued $(g,n)$-dependent differential operator on the
moduli space, encoding the genus-by-genus quantum corrections to
the holographic correspondence.  The genus-$0$ arity-$n$ shadow
$\operatorname{Sh}_{0,n}(\Theta_{M2})$ has the expected
KZ/BPZ-type leading behavior for the $\mathfrak{psl}(2|2)$
benchmark surface; the genus-$1$ shadow
carries the one-loop anomaly $\kappa(\cA_{M2,\infty})\cdot\omega_1$;
higher-genus shadows encode the multi-loop holographic amplitudes.

The quartic contact invariant $Q^{\mathrm{contact}}_{M2}$
is the first obstruction to planarity in the holographic genus
expansion: it is the first invariant that distinguishes the
full string-theoretic amplitude from its planar ($N\to\infty$)
limit.  The modular Koszul datum $\mathcal H(M2)$ packages the
complete holographic correspondence (boundary algebra, bulk
reconstruction, line operators, braiding, genus tower, and
anomaly cancellation) into a single MC problem.

\bigskip
\noindent
\emph{Summary.}\enspace
Sections~1--2 constructed the bar complex and its genus tower from
the logarithmic propagator and the Arnold relation.
Sections~3--4 identified these as projections of a single chain-level
object: the modular convolution $L_\infty$-algebra and its
universal MC element~$\Theta_\cA$.
Sections~5--6 extracted the full hierarchy of characteristic
invariants from~$\Theta_\cA$ and classified chiral algebras by
shadow depth.
Section~7 tested the machine on every standard family.
Section~8 lifted the shadow obstruction tower into number theory: Dirichlet--sewing
series, Euler--Koszul classification, the two-variable $L$-object, and
the arithmetic packet connection.
Section~9 proved one-channel line concentration on the
simple-Lie-symmetry locus, the scalar package on the proved scalar
lane, and assembled the Koszulness programme.
Sections~10--11 transported the machine to three dimensions:
the bar differential became holomorphic factorization, the coproduct
became topological factorization, and the pair became a
Swiss-cheese coalgebra whose PVA shadow governs the deformation
quantization of Poisson vertex algebras to vertex algebras.
Section~12 packaged the entire holographic correspondence into a
six-component modular Koszul datum controlled by a single MC equation.


% ====================================================================
\section*{13.\quad Completion and the frontier}
% ====================================================================

The holographic datum of Section~12 packages a chiral algebra, its Koszul dual, the line-operator
category, the spectral $R$-matrix, the universal MC element, and
the shadow connection into a single algebraic object.  The
frontier consists of structural questions the packaging
forces: the completed bar-cobar problem
by infinite-type algebras, the analytic sewing problem
by genus $g \ge 1$ curvature, the factorization-envelope
problem by the passage from Lie conformal input to
modular output, and the non-principal duality problem
by Drinfeld--Sokolov reduction.

\subsection*{13.1.\enspace The Maurer--Cartan frontier}

All five master conjectures are proved.  MC3 holds for all simple types on the evaluation-generated core via multiplicity-free $\ell$-weights (Theorem~\ref{thm:categorical-cg-all-types}, Corollary~\ref{cor:mc3-all-types}).  The residual problem DK-4/5 (extension beyond evaluation modules) is downstream.

\medskip
\noindent\textbf{MC1} (PBW concentration).
For every standard family (Kac--Moody, Virasoro, principal
$\mathcal W_N$, $\beta\gamma$, lattice) and every genus
$g\ge 1$, the PBW spectral sequence for the genus-$g$ bar
complex has concentrated $E_\infty$ page:
$E_\infty^{p,q}(g)=0$ for $q\neq 0$.

The proof has two steps.  First, genus-$0$ Koszulness supplies
concentration of $E_1^{p,q}(g{=}0)$: the bar complex at genus~$0$
is formal, and the bar-cobar spectral sequence collapses at $E_2$
(this is the definition of chirally Koszul).  Second, the genus-$g$
enrichment $\cE^{p,q}_g$ from the Hodge bundle is
$d_0^{\mathrm{PBW}}$-exact because it arises from the regular
Eisenstein series, which is exact under the Poincar\'e residue map
$\operatorname{Res}\colon H^{q+1}(\overline{\cM}_{g,n},
\Omega^{q+1}_{\log})\to H^q(\sigma_\Gamma,\Omega^q_{\log})$.
The concentration is uniform in the level parameter~$k$: the PBW
filtration is independent of~$k$, and the spectral sequence
differentials are $k$-linear.

\medskip
\noindent\textbf{MC2} (universal $\Theta_\cA$).
The bar-intrinsic construction:
\[
\Theta_\cA\;:=\;D_\cA-d_0
\;\in\;\mathfrak g^{\mathrm{mod}}_\cA
\]
is automatically MC because $D_\cA^2=0$ (the total bar
differential squares to zero).  The MC equation
$d_0\Theta_\cA+\tfrac12[\Theta_\cA,\Theta_\cA]=0$ unpacks to
$D_\cA^2-d_0^2=0$, which holds because both $D_\cA^2=0$
and $d_0^2=0$.

Scalar saturation universality: for every one-parameter algebraic
family $\cA_k$ with rational OPE coefficients,
\[
\Theta_{\cA_k}
\;=\;
\kappa(\cA_k)\cdot\eta_{\mathrm{univ}}\otimes\Lambda_{\mathrm{univ}}.
\]
The higher-order terms in
$H^2_{\mathrm{cyc,prim}}(\cA_k)$ vanish.  Proof: \emph{Whitehead
reduction} computes $H^2_{\mathrm{cyc,prim}}$ via a spectral
sequence whose $E_2$ page is
$H^2(\fg;\operatorname{Sym}^n V)=0$ by the Whitehead lemma for
reductive~$\fg$ (the second cohomology of a semisimple Lie algebra
with coefficients in a finite-dimensional module vanishes).
\emph{Algebraic semicontinuity}: the dimension function
$k\mapsto\dim H^2_{\mathrm{cyc,prim}}(\cA_k)$ is
upper-semicontinuous, vanishes at $k=\infty$ (the free-field
point), and therefore vanishes on a Zariski-dense open set
containing all non-critical levels including admissible ones.

Ambient $D^2=0$: the full differential on the ambient planted-forest
complex (including log-FM strata) satisfies $D^2=0$ by the
normal-crossings result of Mok: the log-FM compactification
$\operatorname{FM}_n(X|D)$ is a manifold with normal-crossings
boundary, and the differential respects the stratification.

\medskip
\noindent\textbf{MC3} (thick generation).
On the type-$A$ Yangian module surface, the four-package MC3
problem reduces to a single remaining compact/completed extension
packet, by the following four steps.
\begin{enumerate}[label=(\alph*)]
\item \emph{Chromatic filtration.}  Stratify the category by
  the support of the $q$-character on the Grothendieck ring.
  The successive quotients $\operatorname{gr}^p_{\mathrm{chrom}}$
  are controlled by products of prefundamental modules at
  chromatic level~$p$.
\item \emph{Prefundamental Clebsch--Gordan.}  The tensor product
  $V_n\otimes L^-$ decomposes as
  $\bigoplus_{j=0}^n L^-(n-2j)$ at the character level, a
  formal series identity $\operatorname{ch}(V_n)\cdot
  \operatorname{ch}(L^-)=\sum_{j=0}^n\operatorname{ch}(L^-(n-2j))$,
  verified to arbitrary depth.  Every Verma character
  $\operatorname{ch}(M(\lambda))$ lies in the $K_0$-span of
  $\{[V_n]\cdot[L^-]\}$.
\item \emph{Completion formalism} (more precisely,
  Francis--Gaitsgory pro-nilpotent completion).  Evaluation
  modules are compact objects (finite composition series in
  $\mathcal{O}^{\mathrm{sh}}$), so once an equivalence on the
  relevant compact core is known, it extends to the corresponding
  ind-completion.
\item \emph{Remaining DK compact/completion packet.}  One still has
  to extend the Koszul duality functor from the evaluation-generated
  core to the compact shifted-prefundamental core, and then compare
  that compact-core equivalence with the relevant ind/pro-nilpotent
  completion.
\end{enumerate}
The CG decomposition part is extended to all simple types
(Theorem~\ref{thm:categorical-cg-all-types}): the multiplicity-free
$\ell$-weight property (Chari--Moura) replaces the minuscule
hypothesis, making the block-separation argument uniform across
all Dynkin types.  The remaining post-CG completion packets are
open beyond type~$A$ (Corollary~\ref{cor:mc3-all-types}).

\medskip
\noindent\textbf{MC4} (completed bar-cobar).
The \emph{strong completion-tower theorem}: the strong filtration
axiom
\[
\mu_r(F^{i_1},\ldots,F^{i_r})
\;\subset\;
F^{i_1+\cdots+i_r}
\]
yields an automatic \emph{arity cutoff}: the $r$-ary operation
maps $F^{i_1}\otimes\cdots\otimes F^{i_r}$ into
$F^{i_1+\cdots+i_r}$, so operations with sufficiently many inputs
land in arbitrarily deep filtration.  For a fixed filtration
degree~$N$, only finitely many arities $r\le N$ contribute to
the $F^N$-piece of the bar-cobar resolution.  This makes
continuity and the Mittag-Leffler condition automatic (no lim${}^1$
obstruction).

The \emph{completion closure}
$\operatorname{CompCl}(\cF_{\mathrm{ft}})$, the full subcategory
of complete filtered objects with finite-type associated graded,
carries a quasi-inverse bar-cobar homotopy equivalence.  The key
results:
\begin{enumerate}[label=(\roman*),nosep]
\item \emph{Coefficient-stability criterion}: convergence of the
  completed bar-cobar reduces to finite matrix stabilisation on
  each graded piece.
\item \emph{MC twisting closure}: the completion closure is stable
  under MC twisting ($\Theta$-twisted objects remain in
  $\operatorname{CompCl}$).
\item \emph{Completed twisting representability}: twisting morphisms
  in the completed setting are representable by the completed
  bar-cobar resolution.
\item \emph{Uniform PBW bridge}: MC1 (PBW concentration) implies
  MC4 (completed bar-cobar) for all standard families via the
  uniform filtration.
\end{enumerate}

MC4 splits into two sub-problems:
\begin{itemize}
\item \emph{MC4${}^+$} (positive towers: $\mathcal W_{1+\infty}$,
  affine Yangians, RTT algebras): solved by weight stabilisation.
  The weight grading provides a natural Cauchy criterion, and the
  completed bar-cobar converges because the bar complex has
  bounded weight in each filtration degree.
\item \emph{MC4${}^0$} (resonant towers: Virasoro, non-quadratic
  $\mathcal W_N$): reduced to a finite resonance problem by the
  resonance-filtered bar-cobar theorem.  The \emph{resonance rank}
  $\rho(\cA)\in\mathbb Z_{\ge 0}\cup\{\infty\}$ measures the
  depth of the resonance: $\rho(\mathcal H_k)=0$,
  $\rho(\widehat{\fg}_k)=0$, $\rho(\beta\gamma)=0$,
  $\rho(\operatorname{Vir}_c)=1$ (the weight-$0$ subspace of the
  bar complex has a one-dimensional resonance at the zero-mode
  of~$L_0$).
\end{itemize}
The \emph{resonance completion theorem}
(Theorem~\ref{thm:platonic-completion}): every positive-energy
chiral algebra has $\rho<\infty$.  The Virasoro case:
$\operatorname{Vir}_{26-c}$ is the depth-zero resonance shadow, the
image of the finite-dimensional resonance truncation~$R_{\mathrm{Vir}}$,
not the final Koszul dual.  The genuine $\mathcal W_\infty$-type
dual requires the full resonance-filtered completion.

\medskip
\noindent\textbf{MC5} (genus expansion).
Proved.  The algebraic genus tower is established together
with the analytic sewing package.  At genus~$0$, the critical-string
algebraic BRST/bar comparison is established, while the top-degree
amplitude pairing remains conditional; bar-cobar inversion
$\Omega(\barB(\cA))\xrightarrow{\sim}\cA$ is Theorem~B.  At genus~$1$,
the curved bar complex with
$d_{\mathrm{fib}}^2=\kappa\cdot\omega_1$ supplies the algebraic
one-loop package, and the complementarity splitting
$Q_1(\cA)\oplus Q_1(\cA^!)=H^*(\overline{\cM}_{1,n},Z(\cA))$
is the genus-$1$ modular-invariance constraint.

At genus $g\ge 2$ the resolution proceeds in five steps.
First, \emph{inductive genus determination}
(Theorem~\ref{thm:inductive-genus-determination}): the genus-$g$
component $\Theta^{(g)}_\cA$ is determined by
$\Theta^{(<g)}_\cA$ via the graph-sum recursion on
$\overline{\cM}_{g,n}$.  Second, \emph{2D convergence}
(Proposition~\ref{prop:2d-convergence}): there is no UV
renormalization on curves: the Feynman integrals
$W_\Gamma=\int_{\sigma_\Gamma}\omega_\Gamma$ converge absolutely
on each stratum $\sigma_\Gamma\subset\overline{\cM}_{g,n}$
without counterterm subtraction.  Third, the \emph{analytic-algebraic
comparison} (Theorem~\ref{thm:analytic-algebraic-comparison}):
$D^{\mathrm{an}}=D^{\mathrm{alg}}$ on the algebraic core, so the
formal graph-sum differential coincides with the analytic one.
Fourth, \emph{general HS-sewing}
(Theorem~\ref{thm:general-hs-sewing}): polynomial OPE growth
together with subexponential sector growth implies the
Hilbert--Schmidt sewing condition, yielding trace-class closed
amplitudes at every genus.  Fifth, the \emph{Heisenberg one-particle
sewing theorem} (Theorem~\ref{thm:heisenberg-one-particle-sewing})
identifies the Heisenberg sewing amplitude with a Fredholm
determinant, providing the decisive first-case verification.
These results resolve the algebraic recursion and analytic convergence
lanes, but not the full genuswise BV/BRST/bar identification.
The correct receptacle remains the coderived category: curvature
at $g\ge 1$ forces coderived/contraderived passage, not ordinary
derived.


\medskip

\noindent\textbf{The completion programme: $q$-windows and completion entropy.}\enspace
The principal $\mathcal{W}_N$-algebra has $N-1$ generators.  The inverse
limit $\mathcal{W}_\infty = \varprojlim_N \mathcal{W}_N$ has
infinitely many, one in each conformal weight $2, 3, 4, \ldots$

The bar-cobar quasi-isomorphism $\Omega(\barB(\cA)) \xrightarrow{\sim} \cA$
is proved for each finite-type stage $\mathcal{W}_N$.  The passage
to the inverse limit requires completed bar-cobar: a filtration
$F^0\cA \supset F^1\cA \supset \cdots$ that makes the bar
differential continuous and the Mittag--Leffler condition
automatic.  The strong filtration axiom
$\mu_r(F^{i_1},\dots,F^{i_r}) \subset F^{i_1+\cdots+i_r}$
achieves this in one stroke: on each quotient $\cA_{\le N}$ only
arities $r \le N$ survive, so the completed differential is
quotientwise finite and the quasi-isomorphism passes to the limit
(Theorem~\ref{thm:completed-bar-cobar-strong}).  The completion
closure $\CompCl(\cF_{\mathrm{ft}})$, the class of all such
inverse limits, carries a quasi-inverse bar-cobar equivalence
stable under Maurer--Cartan twisting.

The completed bar complex decomposes into \emph{finite windows}.
Define the \emph{reduced weight} $\rho(a) := \mathrm{wt}(a) - 1$
for a field of conformal weight $\mathrm{wt}(a)$, and extend
additively to bar words: $\rho(sa_1|\cdots|sa_\ell) = \sum_i
\rho(a_i)$.  The \emph{$q$-window} $K_q(\cA)$ is the span of
bar words of reduced weight $\le q$.

For Virasoro at $q = 2$: the window $K_2(\mathrm{Vir})$ has
basis $\{sT,\; sT|sT\}$, one letter of reduced weight~$1$ and
one two-letter word of total reduced weight~$2$.  The bar
differential on this two-dimensional complex is
$d(sT|sT) = s(T \cdot T)$.  The product $T \cdot T$ decomposes
into the quasi-primary composite $\Lambda = :(TT): -
\tfrac{3}{10}\partial^2 T$, derivatives $\partial^2 T$, and the
central term $\tfrac{c}{2}\cdot\mathbf{1}$.  But $\Lambda$ has
conformal weight~$4$ (reduced weight~$3 > 2$) and $\partial^2 T$
has reduced weight~$3 > 2$, so both project to zero in $K_2$.
Only the central term survives:
\[
d(sT|sT)\big|_{K_2} \;=\; \frac{c}{2}\cdot s\mathbf{1}.
\]
This is $\kappa(\mathrm{Vir}_c) = c/2$ emerging from a
$2 \times 1$ matrix computation.  The curvature is not an abstract
scalar extracted from a theorem; it is the sole surviving
coefficient of the bar differential on the smallest nontrivial
window.

Each window $K_q(\cA)$ depends only on fields of conformal
weight $\le q+1$: a letter in the window has $\mathrm{wt}(a) \le
q+1$, and the bar differential cannot create higher-weight letters
because the OPE estimate
$\mathrm{wt}\,\mu_r(a_1,\ldots,a_r) \le
\sum_i\mathrm{wt}(a_i) - (r-1)$ prevents weight increase.  For the
$\mathcal{W}_N$ tower, $K_q(\mathcal{W}_N)$ stabilises at
$N = q + 1$: the infinite-generator problem is killed exactly, one
window at a time.

The window dimensions grow exponentially.  Define the
\emph{completion entropy} $h_K(\cA) := \log(\rho_\cA^{-1})$,
where $\rho_\cA$ is the radius of convergence of the
primitive generating series
$G_\cA(t) = \tfrac{1-t}{t}(\chi_\cA(t) - 1)$ extracted
from the vacuum character~$\chi_\cA(q)=\mathrm{tr}_\cA(q^{L_0})$
(the graded trace of the Virasoro zero mode).  The entropy
measures kinematic completion complexity: it depends on the
character alone, not on OPE coefficients or curvature.  Its values
form the monotone ladder
\[
h_K(\mathcal{W}_2) \approx 0.567
\;<\; h_K(\mathcal{W}_3) \approx 0.772
\;<\; h_K(\mathcal{W}_4) \approx 0.835
\;<\; \cdots
\;<\; h_K(\mathcal{W}_\infty) \approx 0.872,
\]
governed at the limit by the MacMahon plane-partition generating
function $\chi_{\mathcal{W}_\infty}(q) = \prod_{n \ge 2}(1 -
q^n)^{-(n-1)}$.

\subsection*{13.2.\enspace The analytic frontier}

Curvature forces this direction.  At genus $g \ge 1$ the bar
complex satisfies $d_{\mathrm{fib}}^2 = \kappa \cdot \omega_g
\neq 0$: the ordinary derived category is empty, and the correct
receptacle is the coderived category.  But the coderived passage
requires completed, Hilbert-space-valued structures, not the
bare algebraic OPE data of genus zero.  The analytic frontier asks:
when does the algebraic skeleton extend to a convergent sewing
amplitude?

The bare VOA is a dense algebraic skeleton.  The actual object for
partition functions and sewing is the \emph{sewing envelope}
$\cA^{\mathrm{sew}}$: the Hausdorff completion of~$\cA$ for the
topology defined by all-amplitude seminorms
\[
\|a\|_{\mathrm{amp}}
\;:=\;
\sup_{v\in\cV}\langle v,\pi(a)v\rangle
\]
over suitable families of states~$\cV$.  The algebraic OPE data
embeds densely in $\cA^{\mathrm{sew}}$; the closure provides the
convergent sewing amplitudes needed for genus $g\ge 1$.

The \emph{HS-sewing condition}: if the multiplication operators
$m^c_{a,b}$ are Hilbert--Schmidt in the sense that
\[
\sum_{a,b,c\ge 0}q^{a+b+c}\|m^c_{a,b}\|^2_{\mathrm{HS}}
\;<\;\infty
\]
for $|q|<1$, then the closed amplitudes
$\operatorname{Tr}(\pi(a)\cdot q^{L_0})$ are trace-class and
the sewing operation $\sum_n\langle v_n,\pi(a)w_n\rangle$ converges
absolutely.  The condition is a Hilbert--Schmidt bound on the
OPE coefficients graded by conformal weight.

The \emph{analytic bar coalgebra} $B^{\mathrm{an}}(\cA)$ is the
graph-norm closure of the algebraic bar coalgebra: each bar
element $s^{-1}a_1|\cdots|s^{-1}a_n$ is assigned the norm
$\prod_i\|a_i\|_{\mathrm{amp}}$, and $B^{\mathrm{an}}$ is the
completion in this norm.  An \emph{analytic Koszul pair} is a pair
$(\cA,\cA^!)$ such that the analytic bar-cobar adjunction restricts
to a Quillen equivalence on the sewing-complete categories.

Four targets (two proved, two conjectural):
\begin{enumerate}[label=(\alph*)]
\item \emph{Heisenberg sewing} (the decisive first case):
  the sewing envelope of $\mathcal H_k$ is the ind-Hilbert
  completion
  $\operatorname{Sym}\,A_2(D)\cong\operatorname{ind-Hilb}(\mathcal H_k)$
  (Moriwaki 2026).  The ind-Hilbert structure is the conformally
  flat factorization homology of $\mathcal H_k$ valued in
  $\mathsf{IndHilb}$.
\item \emph{Lattice sewing}: the sewing envelope of $V_\Lambda$
  is the vertex-algebraic completion by lattice theta functions,
  with the theta-function series converging absolutely in the
  sewing-amplitude topology.
\item \emph{Analytic realisation criterion}: a criterion for when
  the algebraic Koszul pair $(\cA,\cA^!)$ extends to an analytic
  one.  The expected criterion: the HS-sewing condition on $\cA$
  plus the dual HS condition on $\cA^!$ should suffice.
\item \emph{Boundary bar duality}: the analytic bar of the
  boundary chiral algebra equals the topological bar of the bulk
  factorization algebra:
  $B^{\mathrm{an}}(\cA_\partial)\simeq
  B^{\mathrm{top}}(\mathrm{Fact}^{\mathrm{bulk}}_T)$,
  identifying the boundary sewing data with the bulk topological
  data.
\end{enumerate}

\subsection*{13.3.\enspace Factorization envelopes and the modular Koszul datum}

The bar construction starts from a chiral algebra, but the natural
input in every geometric construction is a Lie conformal algebra.
The factorization envelope bridges this gap: it is the functor that
produces a chiral algebra from Lie conformal data, and the
programme asks whether the entire modular Koszul package can be
constructed functorially at the Lie conformal level, without
passing through the vertex algebra.  The target is a
universal modular factorization envelope $U^{\mathrm{mod}}_X(L)$
that is left adjoint to extracting primitive currents.

A \emph{cyclically admissible} Lie conformal algebra~$L$
(a $\mathbb C[\partial]$-module equipped with a $\lambda$-bracket
$\{a_\lambda b\}$ satisfying sesquilinearity, skew-symmetry,
and the Jacobi identity) has four
properties: a conformal grading $L=\bigoplus_{\Delta\ge 0}L_\Delta$
by conformal weight, a decreasing filtration
$F^0 L\supset F^1 L\supset\cdots$ compatible with the
$\lambda$-bracket, bounded poles (the $\lambda$-bracket
$\{a_\lambda b\}$ is polynomial in~$\lambda$ of degree bounded by
conformal weights), and an invariant symmetric bilinear pairing
$\langle-,-\rangle\colon L\otimes L\to\mathbb C$ compatible with
the conformal structure.

From a cyclically admissible~$L$, one constructs the
\emph{modular Koszul datum}:
\[
\Pi_X(L)
\;=\;
\bigl(\mathrm{Fact}_X(L),\;\bar B_X(L),\;\Theta_L,\;
\cL_L,\;(V^{\mathrm{br}}_L,T^{\mathrm{br}}_L),\;
R_4^{\mathrm{mod}}(L)\bigr):
\]
the factorization algebra (the Nishinaka factorization envelope),
the bar coalgebra, the universal MC class, the line-operator datum,
the branch-line data, and the quartic resonance class.  Each
component is functorially determined by~$L$.

The target: the \emph{universal modular factorization envelope}
$U^{\mathrm{mod}}_X(L)$ as left adjoint of the modular
primitive-current functor $\operatorname{Prim}^{\mathrm{mod}}$:
\[
\operatorname{Hom}_{\mathsf{Fact}^{\mathrm{mod}}}
\bigl(U^{\mathrm{mod}}_X(L),\,\cF\bigr)
\;\cong\;
\operatorname{Hom}_{\mathsf{LCA}^{\mathrm{cyc}}}
\bigl(L,\,\operatorname{Prim}^{\mathrm{mod}}(\cF)\bigr).
\]
The envelope-shadow functor $\Theta^{\mathrm{env}}_{\le r}(R)$
extracts finite-order shadows from the envelope data: the
universal property of $U^{\mathrm{mod}}_X$ implies that
$\Theta_L=\Theta^{\mathrm{env}}_{\le\infty}(L)$ is the universal
MC class of the modular Koszul datum.

For direct sums $L=L_1\oplus L_2$ with vanishing mixed OPE:
$\kappa(L)=\kappa(L_1)+\kappa(L_2)$ (additivity),
$T^{\mathrm{br}}_L=T^{\mathrm{br}}_{L_1}\oplus T^{\mathrm{br}}_{L_2}$
(direct sum), $\Delta_L=\Delta_{L_1}\cdot\Delta_{L_2}$
(multiplicativity), $R_4^{\mathrm{mod}}(L)
=R_4^{\mathrm{mod}}(L_1)+R_4^{\mathrm{mod}}(L_2)$ (additivity).
BRST reduction on total modular Koszul datums:
the current-plus-ghost package descends to
$\Pi_X(\mathcal W_N)$, hence
$\Theta_{\mathcal W_N}
=H^0_{Q_{\mathrm{DS}}}(\Theta_{V_k(\fg)\otimes F_{\mathrm{gh}}})$:
the shadow obstruction tower of the $W$-algebra is the Drinfeld--Sokolov
reduction of the full current-plus-ghost tower, not of the bare
affine tower alone.

\subsection*{13.4.\enspace Non-principal $W$-algebra duality}

Drinfeld--Sokolov reduction connects the affine landscape to the
$W$-algebra landscape: it takes $\widehat{\mathfrak g}_k$ and a
nilpotent element $f$ and produces the $W$-algebra
$\mathcal W_k(\mathfrak g, f)$.  For principal $f$, the reduction
functor commutes with bar-cobar duality by the Feigin--Frenkel
theorem, and the modular Koszul datum descends.  For non-principal $f$,
this commutation is unproved, and the frontier begins.  The theory
demands this extension because the non-principal $W$-algebras
include the physically central cases ($\mathcal W_k(\mathfrak{sl}_N,
f_{\mathrm{sub}})$ controls $\mathcal N = 2$ superconformal theories)
and the mathematically central ones (the Feigin--Tipunin algebras
at admissible levels).

The hook-type nilpotent orbit in type~$A$ is the first
non-principal corridor for Koszul duality, conditional on
DS-bar compatibility
\textup{(}Theorem~\ref{thm:hook-transport-corridor}\textup{)}.  For a partition
$\lambda=(n-p,1^p)$ (hook type) in $\mathfrak{sl}_N$, the
$W$-algebra $\mathcal W_k(\mathfrak{sl}_N,f_\lambda)$ is defined
by quantum Drinfeld--Sokolov reduction with respect to the
nilpotent element $f_\lambda$.  The duality:
\[
\bigl(\mathcal W_k(\mathfrak{sl}_N,f_\lambda)\bigr)^!
\;\simeq\;
\mathcal W_{k^\vee_\lambda}(\mathfrak{sl}_N,f_{\lambda^t}),
\]
where $\lambda^t$ is the transpose partition and $k^\vee_\lambda$
is the dual level (a rational function of~$k$ depending
on~$\lambda$).  The proof: for hook-type partitions, the DS
reduction functor commutes with bar-cobar duality by the results
of Fehily and Creutzig--Linshaw--Nakatsuka--Sato (2023--2025).

The \emph{transport propagation lemma}: hook-type seeds combined
with edge-compatibility (the property that the DS reduction functor
preserves the collision structure at each FM boundary stratum)
propagate duality results along edges of the nilpotent Hasse
diagram in type~$A$.  The \emph{type-$A$ transport-to-transpose
conjecture}: for every partition~$\lambda$ of~$N$,
$(\mathcal W_k(\mathfrak{sl}_N,f_\lambda))^!
\simeq\mathcal W_{k^\vee_\lambda}(\mathfrak{sl}_N,f_{\lambda^t})$.

The general obstruction is not defining the DS reduction (which
exists for arbitrary nilpotent orbits by Kac--Roan--Wakimoto) but
proving that DS reduction \emph{commutes with the bar-cobar
adjunction}: the natural map
$\mathrm{DS}(\barB(\widehat{\fg}_k))\to
\barB(\mathrm{DS}(\widehat{\fg}_k))$ must be a quasi-isomorphism.
For principal reduction, this follows from the Feigin--Frenkel
theorem; for hook-type in type~$A$, it is conditional on
hook-wide DS-bar compatibility
\textup{(}Theorem~\ref{thm:hook-transport-corridor}\textup{)};
for arbitrary nilpotent orbits, it is the frontier.

\subsection*{13.5.\enspace The boxed machine}

The entire construction can be stated in a single pipeline.
\[
\boxed{
\text{homotopy chiral input }\cA
\;+\;
\text{log-FM cutting cooperad }\mathcal C^!_{\mathrm{ch}}
\;+\;
\text{modular convolution }L_\infty
\;\;\Longrightarrow\;\;
\Theta_\cA,\;
\mathcal T^{\mathrm{mod}}_{\Theta_\cA},\;
\kappa,\;
\Delta_\cA,\;
\mathfrak R^{\mathrm{mod}}_4,\;\ldots
}
\]

\bigskip
\noindent
The modular convolution $L_\infty$-algebra
$\mathfrak g^{\mathrm{mod}}_\cA$ is the single organising structure.
It carries a natural modular $L_\infty$ structure from the Feynman
transform of the modular operad; the dg Lie algebra
$\operatorname{Conv}_{\mathrm{str}}(\mathcal C^!_{\mathrm{ch}},
\mathcal P^{\mathrm{ch}})$ is its strict model.  The universal MC
element
$\Theta_\cA\in\operatorname{MC}(\mathfrak g^{\mathrm{mod}}_\cA)$,
satisfying
\[
D\cdot\Theta_\cA+\tfrac12[\Theta_\cA,\Theta_\cA]\;=\;0,
\]
is proved: it is the bar-intrinsic extraction
$\Theta_\cA:=D_\cA-d_0$, which is MC because $D_\cA^2=0$.

The shadow obstruction tower consists of finite-order projections:
\begin{align*}
\Theta_\cA^{\le 2}&:\qquad\kappa(\cA)
  &&\text{(modular characteristic, scalar curvature)},\\
\Theta_\cA^{\le 3}&:\qquad\mathfrak C(\cA)
  &&\text{(cubic shadow, Lie structure)},\\
\Theta_\cA^{\le 4}&:\qquad\mathfrak Q(\cA)
  &&\text{(quartic resonance class, contact structure)},\\
\Theta_\cA^{\le r}&:\qquad\operatorname{Sh}_r(\cA)
  &&\text{(arity-$r$ shadow)},\\
\Theta_\cA&:\qquad\varprojlim_r\Theta_\cA^{\le r}
  &&\text{(the universal MC element)}.
\end{align*}
Theorems~A--D+H and the genus expansion are proved projections
of the scalar level~$\kappa$.  The holographic datum
$\mathcal H(T)=(\cA,\cA^!,\cC,r(z),\Theta_\cA,\nabla^{\mathrm{hol}})$
is the packaging of $\Theta_\cA$ and its projections into
the data of a 3d holomorphic-topological field theory.  The weight
filtration on $\mathfrak g^{\mathrm{mod}}_\cA$ controls the
extension tower; each finite truncation
$\Theta_\cA^{\le r}$ is constructive and does not require the
full all-genera modular envelope.  The modular tangent complex
extracts Chern--Weil invariants.  The genus spectral sequence
controls the lift across genera.  The standard landscape is
computed.

\begin{principle}[The four-test interface]
\label{princ:four-test-interface}
\index{four-test interface|textbf}%
The modular Koszul machine has a complete algebraic-geometric
interface with $\overline{\mathcal M}_{g,n}$, consisting of
four independent proved tests:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item $D_\cA^2 = 0$:
  the bar differential squares to zero at all genera and arities
  \textup{(}Theorems~\textup{\ref{thm:bar-modular-operad},
  \ref{thm:quantum-diff-squares-zero}}\textup{)}.
\item $\mathrm{obs}_g(\cA) = \kappa(\cA)\cdot\lambda_g$
  for uniform-weight algebras at all genera,
  and unconditionally at genus~$1$ for all families:
  the genus-$g$ obstruction factors as modular characteristic
  times Hodge class
  \textup{(}Theorem~\textup{\ref{thm:modular-characteristic}}\textup{)}.
\item $Q_g(\cA)+Q_g(\cA^!)=H^*(\overline{\mathcal M}_g,Z(\cA))$:
  complementarity assembles the Koszul pair into a Lagrangian
  decomposition
  \textup{(}Theorem~\textup{\ref{thm:quantum-complementarity-main}}\textup{)}.
\item Sewing:
  genus-$g$ amplitudes converge from lower-genus data
  \textup{(}Theorem~\textup{\ref{thm:general-hs-sewing}}\textup{)}.
\end{enumerate}
Each test captures a distinct aspect: \textup{(i)} is purely
algebraic and requires no Koszulness hypothesis;
\textup{(ii)} identifies the tautological class but does not
involve~$\cA^!$; \textup{(iii)} requires the Koszul pair but is
genus-by-genus; \textup{(iv)} is analytic and independent of the
Hodge-class identification.  Any three can hold with the fourth
failing.  Three regions lie outside: multi-weight algebras at
$g\ge 2$ \textup{(}Open Problem~\textup{\ref{op:multi-generator-universality}}\textup{)},
BV/BRST${}={}$bar at higher genus
\textup{(}Conjecture~\textup{\ref{conj:master-bv-brst}}\textup{)},
and non-perturbative completion.
See Remark~\textup{\ref{rem:four-test-interface}} for the full
discussion.
\end{principle}

\medskip
\noindent\textbf{The holographic frontier.}
The holographic datum $\mathcal H(T)$ is a boundary object.
Its lift to a genuine $3$d bulk theory is controlled by the
\emph{relative holographic deformation complex}
$\mathfrak{h}_T^\Theta:=\operatorname{fib}(
\mathfrak{g}_T^{\mathrm{SC}}\to\gAmod)_{\alpha_T}$
(Definition~\ref{def:relative-holographic-deformation}):
lifts of~$\Theta_\cA$ to full bulk/boundary/line data are
exactly MC elements of the twisted fibre
(Proposition~\ref{prop:lifts-as-relative-mc}).
The graded obstruction tower
$[\mathfrak{o}_r(\beta)]
\in H^2(\operatorname{gr}^F_r\mathfrak{h}_T^\Theta)$
turns the holographic frontier into a computable cohomology
calculus.  At depth~$4$, the \emph{relative quartic
obstruction} $\mathfrak{R}_4^{\mathrm{rel}}(T)$
is the first invariant detecting when a boundary datum
cannot arise from a planar holographic realization
(Conjecture~\ref{conj:relative-quartic-computation}).
The \emph{Loop--Connes principle}
$\beta_{\mathrm{der}}^*(\Delta_{\mathrm{open}})=\Lambda_P$
(Conjecture~\ref{conj:loop-connes-transfer}):
closed genus creation is the image of the open BV operator
under the derived-center map; loops in the bulk are traces
on the boundary.

\medskip
\noindent\textbf{Cyclic trace, ribbon structure, and $1/N$.}
A bare modular graph sum does not define a literal
't~Hooft expansion
(Lemma~\ref{lem:bare-graph-no-thooft}).
Cyclic trace structure on the open
$E_1$-chiral algebra resolves this: cyclicity enables ribbon
thickening
(Theorem~\ref{thm:cyclicity-ribbon}),
and a matrix realisation gives the exact weight
$N^{\chi(\Sigma_\Gamma)}$
(Theorem~\ref{thm:exact-n-chi-weighting}).
The three levels of language (plain modular $E_1$
(genus expansion), cyclic traced modular $E_1$ ('t~Hooft
expansion), ribbonised modular Swiss-cheese (holographic
open/closed 't~Hooft language)) are made precise in the
$E_1$ modular Koszul chapter
(Chapter~\ref{chap:e1-modular-koszul}).

\subsection*{13.6.\enspace Admissible levels and logarithmic CFT}

At admissible levels $k = -h^\vee + p/q$ (coprime $p \ge h^\vee$,
$q \ge 1$), the Zhu algebra $A(\mathcal{V}_k(\mathfrak g))$ is
semisimple but the vertex algebra itself is not simple: there is a
maximal proper ideal~$J_k$ with $L_k(\mathfrak g) =
\mathcal{V}_k(\mathfrak g)/J_k$ the simple quotient.  The bar
complex of~$\mathcal{V}_k$ acquires a periodic CDG structure indexed
by the $q$-th roots of unity: the curvature $m_0 = \kappa \cdot
\omega_g$ factors through the cyclotomic polynomial
$\Phi_q(\zeta)$, and the weight filtration has a finite plateau at
level $N = q$.  This is the algebraic door to logarithmic conformal
field theory on the degenerate admissible lane, where the simple
quotient $L_k(\mathfrak g)$ has a logarithmic
\textup{(}non-semisimple\textup{)} module category.  On the
non-degenerate admissible lane the simple quotient is rational,
while the bar-side admissible analysis records vacuum null vectors
and nilradical data as the obstruction surfaces across the broader
admissible picture.  One still has weightwise finite-page
character-theoretic degeneration on the non-degenerate lane,
whereas an identification of the resulting bar
cohomology with logarithmic extensions is not proved here.

\subsection*{13.7.\enspace The relative Feynman transform}

The modular bar coalgebra $\barB_{\mathrm{mod}}(\cA)$ is naturally
an algebra over the relative Feynman transform
$\mathrm{FT}_{\mathsf{Com}_{\mathrm{mod}} /
\mathsf{SC}^{\mathrm{ch,top}}}$.
This is the algebraic skeleton shared by the factorization approach
(\S10.8) and the operadic approach (\S3): the factorization structure
on $\operatorname{Ran}(\Sigma_g) \times \operatorname{Ran}(\mathbb R)$
over $\overline{\cM}_g$ produces it via families of factorizable
$\mathcal D$-modules; the operadic structure on
$\mathsf{SC}^{\mathrm{ch,top}}_{\mathrm{mod}}$ produces it via
formal completion at collision points.

\medskip
\noindent\textbf{Recognition.}\enspace
$\barB_{\mathrm{mod}}(\cA)$ is naturally a
$\mathrm{FT}_{\mathsf{Com}_{\mathrm{mod}} /
\mathsf{SC}^{\mathrm{ch,top}}}$-algebra:
the tree-level part $D_0$ is the
$\mathsf{SC}^{\mathrm{ch,top}}$-coalgebra structure, and the
genus-raising part $D_1$ is the
$\mathsf{Com}_{\mathrm{mod}}$-modular structure.

\medskip
\noindent\textbf{Homotopy-involutivity.}\enspace
$\mathrm{FT}_{\mathsf{Com}_{\mathrm{mod}} /
\mathsf{SC}^{\mathrm{ch,top}}}^{\;2} \simeq \mathrm{id}$.
The proof proceeds in three steps:
genus-$0$ involutivity from operadic homotopy-Koszulity
(the homotopy-Koszulity theorem, Vol~II),
closed-colour modular involutivity from the Feynman involution
(Theorem~\ref{thm:feynman-involution}),
and assembly via the genus-filtration spectral sequence.

\medskip
\noindent\textbf{Three routes unified.}\enspace
Route~B (factorization, \S10.8) provides the global truth:
factorization on $\operatorname{Ran}(\Sigma_g) \times
\operatorname{Ran}(\mathbb R)$ over $\overline{\cM}_g$.
Route~A (operadic, \S3) provides the local approximation:
$\mathsf{SC}^{\mathrm{ch,top}}_{\mathrm{mod}}$ at formal
completions.  Route~C (this section) provides the algebraic
skeleton: $\mathrm{FT}_{\mathsf{Com}_{\mathrm{mod}} /
\mathsf{SC}^{\mathrm{ch,top}}}$ as the common abstraction.
The factorization structure projects to the relative Feynman
transform by forgetting $\mathcal D$-module data; the operadic
structure injects into it by formal completion.  The relative
Feynman transform is the categorical image.

\subsection*{13.8.\enspace The computational infrastructure}

Every formula in this preface has been verified by an independent
symbolic computation layer comprising tens of thousands of tests
across several hundred modules, covering the shadow obstruction tower through
arity~$32$, the
standard landscape for all seven families, the genus-$2$ and
genus-$3$ planted-forest formulas, the DS-shadow cascade
(arities~$2$--$8$ for $N=2,\ldots,5$), the W$_3$ multi-generator
shadow metric on the $(T,W)$-plane, the B\"ocherer bridge at
genus~$2$, the Pixton shadow bridge, the entanglement programme
(Page curve, holographic codes), the non-simply-laced bar
computations ($B_2$/$C_2$/$G_2$/$F_4$), minimal model bar and
fusion rules, the dressed propagator engine (scalar
complementarity, $R$-matrix $R_1=1/12$), and the constrained
Epstein zeta for lattice VOAs.  The computation is adversarial:
tests encode cross-family consistency checks (additivity,
complementarity, anti-symmetry) that cannot be fooled by a single
hardcoded value.

Volume~II develops the $3$d theory in three new chapters: the
factorization Swiss-cheese algebra (the global truth on
$\operatorname{Ran}(\Sigma_g)\times\operatorname{Ran}(\mathbb R)$),
the modular Swiss-cheese operad (the local approximation at formal
completions), and the relative Feynman transform (the algebraic
skeleton connecting both).  These chapters, together with the
$3$d gravity chapter (six movements: from the Koszul triangle to
anomaly-completed MC recursion at all genera), the affine half-space
BV theorem (from linear to nonlinear via the doubling principle),
and eleven additional computational engines, constitute the
Volume~II programme.

\subsection*{13.9.\enspace The single open problem}

Everything proved in this monograph is a finite-order projection
of the universal MC element
$\Theta_\cA \in \MC(\mathfrak{g}^{\mathrm{mod}}_\cA)$.
Everything open is a question about its ambient:

\begin{center}
\fbox{\parbox{0.85\textwidth}{\centering
\emph{Characterise the modular convolution algebra
$\mathfrak{g}^{\mathrm{mod}}_\cA$ as a geometric object.}
}}
\end{center}

\noindent
Precisely: the modular convolution algebra is the endomorphism
algebra of the Lagrangian embedding
$\cL_\cA \hookrightarrow \cM_{\mathrm{vac}}(\cA)$ in the
$(-2)$-shifted symplectic stack of vacua.  Volume~I computes
the Taylor jets of this embedding (the shadow obstruction tower).
Volume~II identifies the local composition law (the Swiss-cheese
operad).  What remains is the global geometry of the stack itself:
the derived symplectic structure, the moduli of Lagrangians, and
the higher-categorical descent that would make the construction
independent of choices.

The ${\sim}150$ open conjectures in these two volumes are projections
of this single question:
\begin{itemize}[nosep]
\item the D-module purity conjecture asks whether the Lagrangian
  is pure (characterisation (xii) of Koszulness);
\item the non-principal W-duality programme asks how the Lagrangian
  transforms under Drinfeld--Sokolov reduction at arbitrary
  nilpotent orbits;
\item the analytic completion programme asks when the algebraic
  Lagrangian extends to a convergent one (the sewing envelope);
\item the factorization envelope programme asks for the universal
  construction of the Lagrangian from Lie conformal data alone;
\item the holographic completion question asks whether the genus-$0$
  Lagrangian extends over $\overline{\cM}_{g,n}$ (the modular
  programme of Volume~II).
\end{itemize}
Each is a different facet of the geometry of
$\mathfrak{g}^{\mathrm{mod}}_\cA$, and none requires going
beyond the framework already established.

\bigskip

\noindent
The entire structure unfolds from a single datum: the logarithmic
$1$-form $\eta = d\log(z_1 - z_2)$.  At $n$~points it became a
differential on the Fulton--MacPherson compactification; across all
genera it became the total bar differential~$D_\cA$; in the modular
convolution algebra it became the Maurer--Cartan element
$\Theta_\cA = D_\cA - d_0$.  One $1$-form, one relation (Arnold),
one extraction (residues): a universal invariant of chiral algebras
that is algebraic, computable, and complete.
