% Preface Sections 10--13: The Open/Closed World through Frontier
% Draft for integration into preface.tex
% Replaces the current closing sections (lines 237--352 of preface.tex)

\bigskip

\noindent\textbf{The open/closed world (Volume~II).}
The bar complex lives naturally in three dimensions.  On the product
$\mathbb C_z \times \mathbb R_t$, the holomorphic direction along
$\mathbb C$ produces the closed-string bar differential: collisions of
points in the holomorphic plane extract OPE residues.  The topological
direction along $\mathbb R$ produces the open-string coproduct: the
ordered splitting of tensor factors at a cut point of the real line.
The Swiss-cheese operad $\SCchtop$ encodes the interaction of these two
structures.  The resulting two-colour algebraic framework is the
bar complex's natural habitat: without the topological direction, the
coproduct has no operadic home, and the line-operator category has no
definition.

The primitive object of three-dimensional holomorphic-topological
quantum field theory on $\mathbb C_z \times \mathbb R_t$ is the
open/closed factorization dg-category~$\mathcal C$ on the bordified
curve~$\widetilde{X}_D$.  Its objects are boundary conditions, its
morphisms are open-string states, and a choice of vacuum~$b$ yields a
boundary algebra $A_b = \operatorname{End}_{\mathcal C}(b)$, determined
only up to Morita equivalence.  The bar complex of Volume~I is the
coalgebraic shadow of this category: its differential records how
closed-sector operations twist the open-sector composition, and its
coproduct records the ordered splitting of the topological direction.

Three independent objects are constructed from~$\mathcal C$:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item the \emph{bar complex} $\barB(A_b)$ classifies couplings
  between $A_b$ and~$A_b^!$ (twisting morphisms);
\item the \emph{chiral derived center}
  $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\mathcal C) =
  R\!\operatorname{Hom}_{\operatorname{Fun}(\mathcal C,\mathcal C)}
  (\operatorname{Id}, \operatorname{Id})$
  is the universal bulk, computed in any chart by chiral Hochschild
  cochains $C^\bullet_{\mathrm{ch}}(A_b, A_b)$;
\item the \emph{Koszul dual} $A_b^!$ governs the line-operator
  category $\cA^!\text{-}\mathsf{mod}$ with its spectral braiding
  $R(z)$.
\end{enumerate}
The primitive hierarchy is:
\[
\mathcal C_{\mathrm{op}}
\;\xrightarrow{\;\operatorname{End}(b)\;}
A_b
\;\xrightarrow{\;\barB\;}
\barB(A_b)
\;\xrightarrow{\;\Theta\;}
\Theta_\cA
\;\xrightarrow{\;+\mu^{M_j}\;}
\Theta^{\mathrm{oc}}_\cA.
\]
Each arrow is a lossy functor: $\mathcal C_{\mathrm{op}}$ is
Morita-invariant; $A_b$ depends on the boundary
condition~$b$; $\barB$ forgets the bulk; $\Theta_\cA$ is the
closed-sector MC element; $\Theta^{\mathrm{oc}}_\cA$ restores the
full open/closed package.

The operad $\SCchtop$ is homotopy-Koszul (proved).  The operation spaces
are $\SCchtop(\mathrm{ch}^k;\mathrm{ch})=\operatorname{FM}_k(\mathbb C)$,
$\SCchtop(\mathrm{ch}^k,\mathrm{top}^m;\mathrm{top})
=\operatorname{FM}_k(\mathbb C)\times E_1(m)$, and
$\SCchtop(\ldots,\mathrm{top},\ldots;\mathrm{ch})=\varnothing$:
open-to-closed is forbidden.  A bar element of tensor degree~$k$ lives on
$\operatorname{FM}_k(\mathbb C)\times\operatorname{Conf}_k(\mathbb R)$:
the bar differential extracts OPE residues along collision divisors of the
first factor, and the coproduct splits an ordered sequence at a cut point
of the second factor.  Kontsevich formality supplies a
quasi-isomorphism $\Phi\colon\SCchtop\xrightarrow{\sim}\mathsf{SC}$ from
the holomorphic-topological operad to the classical Swiss-cheese operad,
and the bar-cobar adjunction on $\SCchtop$-algebras is a Quillen
equivalence.  Three consequences: every $\SCchtop$-algebra admits a
cofibrant replacement by bar-cobar resolution; the homotopy category of
$\SCchtop$-algebras is equivalent to that of coalgebras over the Koszul
dual cooperad; and the line-operator category
$\cA^!\text{-}\mathsf{mod}$ is unconditionally defined as a module
category over the bar resolution.

On cohomology $H^\bullet(\cA,Q)$, the $\SCchtop$ operations simplify by
dimension.  The regular part of~$m_2$ is a commutative product~$\mu$
(commutativity from the $\mathbb Z/2$-involution on
$\operatorname{FM}_2(\mathbb C)$).  The singular part is a
$\lambda$-bracket $\{a_\lambda b\}=\sum_{n\ge 0}\lambda^{(n)}a_{(n)}b$
(the exponential residue extracts all pole orders simultaneously).  All
$m_k=0$ for $k\ge 3$ on $H^\bullet$: the topological factor
$\operatorname{Conf}_k(\mathbb R)$ is contractible for $k\ge 3$, so
higher operations are $d_{\mathbb R}$-exact and therefore trivial.  The
Jacobi identity descends from the Arnold relation on
$\operatorname{FM}_3(\mathbb C)$; the Leibniz rule from the three-face
Stokes identity on the boundary of
$\operatorname{FM}_3(\mathbb C)$; skew-symmetry from
the exchange monodromy on $\operatorname{FM}_2(\mathbb C)\times E_1(2)$.
Each axiom of the Poisson vertex algebra $(\mu,\{-_\lambda-\})$ follows
in one line from the geometry of FM spaces.

For the Heisenberg algebra $\mathcal H_k$ in Swiss-cheese coordinates:
$\{J_\lambda J\}=k\lambda$, $m_n=0$ for $n\ge 3$, and the regular
product $\mu(J,J)={:}JJ{:}$ is the normal-ordered square.  The sole
singular OPE mode is $J_{(1)}J=k$; the first-order pole $J_{(0)}J$
vanishes, so configuration-space integrals at arity $n\ge 3$ factor
through the single datum $J_{(1)}J=k$ and yield zero by degree
considerations.  The spectral $R$-matrix is $R(z)=\exp(k/z)$; the
Yang--Baxter equation is trivially satisfied (the $R$-matrix is
scalar).

The Koszul triangle relates the three objects constructed
from~$\mathcal C$: the boundary algebra
$A_b=\operatorname{End}_{\mathcal C}(b)$ (an $E_1$ chart, Morita-dependent),
the bulk $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\mathcal C)\simeq
\operatorname{HH}^\bullet(A_b)$
(Morita-invariant; Koszul-dual to
$\mathrm{ChirHoch}^{\bullet-2}(A_b^!)^\vee\otimes\omega_X$
by Theorem~H), and the lines
$A_b^!\text{-}\mathsf{mod}$ with spectral braiding
$R(z)\colon L_1\otimes L_2\xrightarrow{\sim}L_2\otimes L_1$.
The spectral braiding satisfies the Yang--Baxter equation because
Stokes' theorem on $\operatorname{FM}_3(\mathbb C)$ decomposes
the boundary into three pairwise collision divisors, one for each side
of the YBE.  The bar complex classifies twisting morphisms and is not
the bulk; the derived center classifies bulk operators acting on the
boundary.

Volume~II identifies the geometric substrate of the bar construction:
the bar complex is the structure sheaf of the Lagrangian
self-intersection
$\mathfrak{S}=\mathcal{L}\times_{\mathcal{M}}\mathcal{L}$
in a $(-2)$-shifted symplectic stack.  The bar-cobar adjunction
(Theorem~A) is the groupoid comodule-module adjunction for~$\mathfrak{S}$;
Koszul inversion (Theorem~B) reconstructs the Lagrangian from its clean
self-intersection; complementarity (Theorem~C) is two Lagrangians whose
intersection carries a $(-1)$-shifted symplectic structure; the modular
characteristic (Theorem~D) is the Kodaira--Spencer class of the
Lagrangian family over the Hodge bundle; and the Hochschild polynomial
growth (Theorem~H) is the HKR theorem for the Lagrangian embedding.

At genus $g\ge 1$ the bar complex acquires curvature:
$d_{\mathrm{fib}}^{\,2}=\kappa(\cA)\cdot\omega_g$.  The curvature lives
entirely in the holomorphic direction; the topological $E_1$-structure
on~$\mathbb R$ sees no curvature (the interval has no nontrivial
topology).  The total corrected differential
$D_g=d_{\mathrm{fib}}+\nabla^{\mathrm{GM}}_g$ restores flatness over
$\overline{\cM}_g$: the Gauss--Manin connection absorbs the
$(1,1)$-curvature.  Curvature forces the coderived category
$\mathsf{D}^{\mathrm{co}}(\cA^{(g)})$ as the correct receptacle: the
ordinary derived category is empty (every object is acyclic), while the
coderived category, defined via totalisation of the curvature bicomplex,
retains the correct homotopy theory.

Volume~II constructs this architecture in four stages:
\emph{Stage~1} (local one-colour theorem: derived center is universal
bulk; proved) $\Rightarrow$
\emph{Stage~2} (open primitive: $\mathcal C$ with Morita invariance;
proved) $\Rightarrow$
\emph{Stage~3} (globalization on tangential log curves
$(X,D,\tau)$; proved locally) $\Rightarrow$
\emph{Stage~4} (modularization: trace plus clutching producing
$\Theta^{\mathrm{oc}}$; annulus trace proved, full chain-level clutching
is programme).
The genus expansion of $\Theta^{\mathrm{oc}}_\cA$ yields the
perturbative free energies~$F_g$; the shadow archetypes
$\mathsf{G}/\mathsf{L}/\mathsf{C}/\mathsf{M}$ classify the nonlinear
complexity of the Swiss-cheese operations.

Five negative principles constrain the architecture:
\begin{enumerate}[label=\textup{N\arabic*.},nosep]
\item \emph{Bar $\neq$ bulk.}
  $\barB(A_b)$ classifies twisting morphisms.
  $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\mathcal C)$ classifies bulk
  operators.  Different functors, different outputs.
\item \emph{Boundary algebra $=$ chart.}
  $A_b = \operatorname{End}_{\mathcal C}(b)$ depends on $b$.  Only
  $\mathcal C$ and its derived center are intrinsic.
\item \emph{Tangential log geometry required.}
  The bordified curve $\widetilde{X}_D$ is a manifold with corners
  on an snc pair $(X,D)$.  Ordinary FM is the $D = \varnothing$
  special case.
\item \emph{Modularity $=$ trace $+$ clutching on the open sector.}
  The genus expansion is not an additional axiom on the closed
  algebra; it is determined by the cyclic trace on
  $\operatorname{End}_{\mathcal C}(b)$ and the gluing along
  boundary circles.
\item \emph{Honest scope.}
  Thick generation (MC3) is proved for all simple types on the
  evaluation-generated core.  Extension beyond evaluation modules
  (DK-4/5) and the full holographic datum for non-standard families
  are programme, not theorem.
\end{enumerate}

\bigskip

\noindent\textbf{Modular PVA quantization.}
The Swiss-cheese structure at genus~$0$ produces a Poisson vertex
algebra $(\mu,\{-_\lambda-\})$ on the cohomology $H^\bullet(\cA,Q)$:
the commutative product~$\mu$ from the regular part of the OPE, the
$\lambda$-bracket from the singular part, the Jacobi identity from
Arnold on $\operatorname{FM}_3(\mathbb C)$.  All of this is tree-level.
The question is whether the tree-level PVA extends to a quantum
algebra at genus~$g\ge 1$, and the answer is controlled by an
obstruction theory whose structure mirrors the geometry of stable
curves.

The total bar differential $D=D_0+D_1$ decomposes by the topology
of node degenerations.  A stable curve of genus~$g$ degenerates by
either a \emph{separating} node (the curve splits into two
components of genera $g_1+g_2=g$, total genus preserved) or a
\emph{nonseparating} node (the curve acquires a self-crossing,
genus dropping by~$1$).  Set $D_0:=d_{\mathrm{int}}+d_{\mathrm{sep}}$
(the tree-level differential plus separating degenerations) and
$D_1:=d_{\mathrm{nsep}}$ (nonseparating degenerations alone).  The
identity $(D_0+D_1)^2=0$ stratifies by genus shift:
\[
D_0^2=0,
\qquad
D_0 D_1+D_1 D_0=0,
\qquad
D_1^2=0.
\]
The three identities have three meanings.  $D_0^2=0$: the tree-level
differential is a differential; this is chirality, the content of the
Borcherds identity.  $D_0 D_1+D_1 D_0=0$: the loop operator $D_1$
anticommutes with the tree-level differential, so it descends to a
well-defined map on $D_0$-cohomology; the genus-one obstruction
\[
\operatorname{Ob}_1(\Theta_0)
\;=\;
[D_1\Theta_0]
\;\in\;
H^2\!\bigl((\operatorname{gr}^1_F L)^{\Theta_0},\,d_0^{\Theta_0}\bigr)
\]
is a cohomology class, not a cochain.  $D_1^2=0$: the loop
operator squares to zero, so the genus-two obstruction is a
class in the $D_1$-cohomology of the genus-one lift, and the
tower propagates.  Trees govern chirality; loops govern
modularity.

In PVA coordinates, $D_1$ acts as the reduced odd Laplacian
$\Delta_{\mathrm{cyc}}(a)=\sum_i m_2(e^i,m_2(a,e_i))$: contract
two legs of a cyclic cochain over a single loop, raising genus
by~$1$ and lowering arity by~$2$.  This is the shadow-level
incarnation of the BV operator.  For the Heisenberg PVA:
$\Delta_{\mathrm{cyc}}(J\otimes J)=k$, and all higher
obstructions vanish since $\Delta_{\mathrm{cyc}}(k)=0$.  The
genus-one lift is unique; the genus expansion terminates.  For
the classical $\mathcal W_3$ PVA: the obstruction cohomology
$H^2((\operatorname{gr}^1 L)^{\Theta_0},d_0^{\Theta_0})$ is
one-dimensional, spanned by the deformation
$\partial_c P_c$ of the central charge.  Every genus-one lift
is gauge-equivalent to a renormalisation
$c\mapsto c+\hbar c_1$: the quantum $\mathcal W_3$ algebra at
genus~$1$ is unique up to a shift of central charge.

The full genus tower is the BV quantum master equation in
curved form:
$\hbar\,\Delta(e^{(S+\alpha)/\hbar})=0$.
At genus~$0$ this is the curved $A_\infty$ MC equation with
$m_0=S$.  At genus~$1$: vanishing of the curved odd Laplacian.
At genus~$g$: the QME itself, with each genus-$g$ component
determined by lower genera via the graph-sum recursion.  The
quantisation pipeline:
\[
\underbrace{(\mu,\{-_\lambda-\})}_{\text{classical PVA
(genus $0$, tree-level)}}
\;\xrightarrow{\;\operatorname{Ob}_1=0\;}
\underbrace{\cA_\hbar}_{\text{quantum algebra
(genus $1$, one-loop)}}
\;\xrightarrow{\;D_1^2=0\;}
\underbrace{\mathcal H(T)}_{\text{holographic datum
(all genera)}}.
\]

\bigskip

\noindent\textbf{Holographic modular Koszul duality.}
Every three-dimensional holomorphic-topological system~$T$ is
controlled by a \emph{holographic modular Koszul datum}
\[
\mathcal H(T)
\;=\;
\bigl(\cA,\;\cA^!,\;\cC,\;r(z),\;\Theta_\cA,\;\nabla^{\mathrm{hol}}\bigr),
\]
with components: $\cA$ the boundary chiral algebra, $\cA^!$ the strict
chiral Koszul dual (a dg-shifted Yangian in the holographic setting),
$\cC\simeq\cA^!\text{-}\mathsf{mod}$ the braided tensor category of line
operators, $r(z)=\operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$
the spectral $R$-matrix (the binary genus-$0$ shadow of~$\Theta_\cA$),
$\Theta_\cA$ the universal MC element, and
$\nabla^{\mathrm{hol}}_{g,n}=d-\operatorname{Sh}_{g,n}(\Theta_\cA)$ the
modular shadow connection (flat by the MC equation projected to genus~$g$
and arity~$n$).  The datum is the natural unit of holographic data: the
smallest package from which the full correspondence can be reconstructed.

The modular convolution algebra $\gAmod$
carries a \emph{collision filtration}
$F^0_{\mathrm{coll}}\supset F^1_{\mathrm{coll}}\supset\cdots$
indexed by the minimum pairwise distance on
$\operatorname{FM}_n(\mathbb C)$: depth~$0$ is the
free-propagation regime, depth~$1$ is the first collision stratum,
depth~$k$ is the $k$-fold nested collision locus.  The associated
spectral sequence has $E_1^{0,*}$ the free-field contribution and
$E_1^{1,*}$ the collision residues; the first differentials are
Arnold-type cancellations with $d_1^2=0$ on the $E_1$ page.  Collapse
is governed by shadow depth: class~$\mathbf{G}$ at $E_2$;
class~$\mathbf{M}$ at no finite page.

Four recovery theorems extract lower structures from~$\Theta_\cA$.
\emph{(R1) Collision residue = twisting.}  The depth-$1$ collision
stratum at arity~$2$ extracts the universal twisting morphism:
$\operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)=\pi_\cA$,
producing the dg-shifted Yangian~$r_\cA(z)$.
\emph{(R2) CYBE from Arnold.}  The three boundary divisors of
$\overline M_{0,4}$ correspond to the three channels; evaluating the
Arnold relation on the Casimir tensor produces the three terms of the
classical Yang--Baxter equation.
\emph{(R3) KZ/BPZ comparison.}  For $\cA=\widehat{\fg}_k$, the
genus-$0$ shadow one-form at arity~$n$ is the KZ connection
$\operatorname{Sh}_{0,n}(\Theta_{\widehat{\fg}_k})
=\sum_{i<j}\Omega_{ij}/(h^\vee{+}k)\cdot d\log(z_i{-}z_j)$;
flatness is the MC equation at genus~$0$ and arity~$n$.  For
$\cA=\mathrm{Vir}_c$, the analogous extraction yields the BPZ
differential equations.  The affine Drinfeld--Kohno theorem compares
the braid-group monodromy with the quantum-group braiding.
\emph{(R4) Quartic = $L_\infty$ obstruction.}  The quartic resonance
class $[\mathfrak R^{\mathrm{mod}}_4(\cA)]=[o_4(\cA)]$ is the
obstruction to extending the Yangian seed from arity~$2$ to arity~$4$;
it vanishes for classes $\mathbf{G}$, $\mathbf{L}$, $\mathbf{C}$ and is
nonzero for class~$\mathbf{M}$
($Q^{\mathrm{contact}}_{\mathrm{Vir}}=10/[c(5c+22)]$).

The Khan--Zeng bridge completes the pipeline.  The field content of the
3d holomorphic-topological Poisson sigma model on
$\mathbb R_+\times\mathbb C$: a $\fg$-valued $(0,1)$-form $A_{\bar z}$,
a $\fg^*$-valued scalar~$\phi$, and a $\fg$-valued $1$-form
$\eta$ along~$\mathbb R_+$.  Gauge invariance holds if and only if
the $\lambda$-bracket satisfies PVA Jacobi; the boundary theory on
$\{0\}\times\mathbb C$ carries a $(-1)$-shifted Poisson bracket producing
the genus-zero quantization problem.  The modular extension, coupling the
bulk theory to stable curves via $\cC_g\to\overline{\cM}_g$, controls
the full genus tower of the quantum Koszul datum.  The doubling theorem
embeds every half-space BV problem into the doubled whole-space; the
affine Poisson-vertex sigma model satisfies the hypotheses of the physics
bridge theorem, so the entire standard landscape enters through two
gates: Kac--Moody and Drinfeld--Sokolov reduction.

Three holographic datums illustrate the depth classification.
\emph{Heisenberg} (class~$\mathbf{G}$): $\cA=\mathcal H_k$,
$\cA^!=\mathrm{Sym}^{\mathrm{ch}}(V^*)$, $\cC=\mathsf{Vect}$,
$r(z)=k/z$, $R(z)=\exp(k/z)$; the shadow connection is trivial, all
conjectural targets trivially verified.
\emph{Affine $\widehat{\mathfrak{sl}}_2$} (class~$\mathbf{L}$):
$r(z)=\Omega/z$ (Yang's solution of the CYBE),
$\cC=\mathcal O_q^{\mathrm{sh}}$, $q=e^{i\pi/(k+2)}$; the shadow
connection is KZ, and the Drinfeld--Kohno theorem recovers quantum-group
braiding from genus-$0$ monodromy.
\emph{Virasoro} (class~$\mathbf{M}$):
$r_c(z)=(c/2)/z^3+2T/z$, $\kappa_c=c/2$,
$Q^{\mathrm{contact}}=10/[c(5c+22)]$; the datum packages 3d quantum
gravity on the half-space, with transferred coproduct strictly primitive
at all arities (gravity does not produce particles, only braids them) and
the Koszul dual $\mathrm{Vir}_{26-c}$ (self-dual at $c=13$, not $c=26$).

\bigskip

\noindent\textbf{Completion and the frontier.}
MC1 through MC4 are proved; MC5 is partially proved, with the analytic HS-sewing package at all genera and the genuswise BV/BRST/bar identification conjectural.

\medskip

\noindent\emph{MC1} (PBW concentration).
For every standard family and every genus $g\ge 1$, the PBW spectral
sequence has concentrated $E_\infty$ page: $E_\infty^{p,q}(g)=0$ for
$q\neq 0$.  Genus-$0$ Koszulness supplies the base; the genus-$g$
enrichment from the Hodge bundle is $d_0^{\mathrm{PBW}}$-exact by the
Poincar\'e residue map.

\noindent\emph{MC2} (universal $\Theta_\cA$).
The bar-intrinsic construction $\Theta_\cA:=D_\cA-d_0$ is automatically
MC because $D_\cA^2=0$.  For algebraic families with rational OPE
coefficients, rigidity gives the line-concentration
$\Theta_\cA^{\min}=\eta\otimes\Gamma_\cA$ by Whitehead reduction and
algebraic semicontinuity.  The stronger scalar identity
$\Gamma_\cA=\kappa(\cA)\cdot\Lambda_{\mathrm{univ}}$ is proved on the
uniform-weight lane; for multi-weight algebras at $g\ge 2$ the free
energy receives a cross-channel correction $\delta F_g^{\mathrm{cross}}$.
Ambient $D^2=0$ is proved via Mok's log-FM normal-crossings result.

\noindent\emph{MC3} (thick generation).
Proved for all simple types on the evaluation-generated core via
multiplicity-free $\ell$-weights
(Theorem~\ref{thm:categorical-cg-all-types},
Corollary~\ref{cor:mc3-all-types}).  The proof has four steps: chromatic
filtration, prefundamental Clebsch--Gordan, Francis--Gaitsgory
pro-nilpotent completion, and the remaining DK compact/completion packet.
The multiplicity-free $\ell$-weight property (Chari--Moura) replaces the
minuscule hypothesis, making the block-separation argument uniform across
all Dynkin types.

\noindent\emph{MC4} (completed bar-cobar).
The strong filtration axiom
$\mu_r(F^{i_1},\ldots,F^{i_r})\subset F^{i_1+\cdots+i_r}$ yields an
automatic arity cutoff: operations with sufficiently many inputs land in
arbitrarily deep filtration, so continuity and Mittag--Leffler are
automatic.  MC4 splits into MC4${}^+$ (positive towers:
$\mathcal W_{1+\infty}$, affine Yangians, RTT; solved by weight
stabilisation) and MC4${}^0$ (resonant towers: Virasoro, non-quadratic
$\mathcal W_N$; reduced to finite resonance by the resonance-filtered
bar-cobar theorem).  The completed bar complex decomposes into finite
$q$-windows $K_q(\cA)$: for Virasoro at $q=2$, the window
$K_2(\mathrm{Vir})=\operatorname{span}\{sT,\;sT|sT\}$ yields
$d(sT|sT)|_{K_2}=(c/2)\cdot s\mathbf{1}=\kappa(\mathrm{Vir}_c)
\cdot s\mathbf{1}$: the curvature emerging from a
$2\times 1$ matrix computation.

\noindent\emph{MC5} (genus expansion).
The algebraic genus tower is established with the analytic sewing
package.  Five steps: inductive genus determination (genus-$g$ component
determined by lower genera via graph-sum recursion), 2D convergence (no
UV renormalization on curves), analytic-algebraic comparison
($D^{\mathrm{an}}=D^{\mathrm{alg}}$ on the algebraic core), general
HS-sewing (polynomial OPE growth plus subexponential sector growth
implies Hilbert--Schmidt sewing at all genera;
Theorem~\ref{thm:general-hs-sewing}), and the Heisenberg one-particle
sewing theorem (Fredholm determinant;
Theorem~\ref{thm:heisenberg-one-particle-sewing}).  Curvature at
$g\ge 1$ forces the coderived category as correct receptacle; the
full genuswise BV/BRST/bar identification remains conjectural
(Conjecture~\ref{conj:master-bv-brst}).

\medskip

The \emph{analytic frontier} asks: when does the algebraic skeleton
extend to convergent sewing amplitudes?  The sewing envelope
$\cA^{\mathrm{sew}}$ is the Hausdorff completion for all-amplitude
seminorms; the HS-sewing condition gives a Hilbert--Schmidt bound on
OPE coefficients graded by conformal weight.  The analytic bar coalgebra
$B^{\mathrm{an}}(\cA)$ is the graph-norm closure.  Two targets are
proved: Heisenberg sewing (ind-Hilbert completion, Moriwaki 2026) and
lattice sewing (theta-function convergence).  Two remain conjectural:
the analytic realisation criterion and boundary bar duality.

The \emph{factorization-envelope programme} asks whether the entire
modular Koszul package can be constructed functorially at the Lie
conformal level.  The factorization envelope bridges the gap: from a
cyclically admissible Lie conformal algebra~$L$, one constructs the
modular Koszul datum
$\Pi_X(L)=(\mathrm{Fact}_X(L),\barB_X(L),\Theta_L,\cL_L,
(V^{\mathrm{br}}_L,T^{\mathrm{br}}_L),R_4^{\mathrm{mod}}(L))$, each
component functorially determined by~$L$.  The target: a universal
modular factorization envelope $U^{\mathrm{mod}}_X(L)$ as left adjoint
of the modular primitive-current functor.  Drinfeld--Sokolov reduction on
total modular Koszul datums gives
$\Theta_{\mathcal W_N}
=H^0_{Q_{\mathrm{DS}}}(\Theta_{V_k(\fg)\otimes F_{\mathrm{gh}}})$:
the shadow obstruction tower of the $W$-algebra is the DS reduction of
the full current-plus-ghost tower.

The \emph{non-principal W-duality programme} begins where the principal
corridor ends.  For non-principal nilpotent~$f$, the general obstruction
is proving that DS reduction commutes with bar-cobar.  The hook-type
nilpotent orbit in type~$A$ is the first non-principal corridor:
$(\mathcal W_k(\mathfrak{sl}_N,f_\lambda))^!\simeq
\mathcal W_{k^\vee_\lambda}(\mathfrak{sl}_N,f_{\lambda^t})$ for
partitions $\lambda=(n-p,1^p)$, conditional on hook-wide DS-bar
compatibility (Theorem~\ref{thm:hook-transport-corridor}).  The
transport propagation lemma carries duality along edges of the
nilpotent Hasse diagram in type~$A$.

\bigskip

\noindent\textbf{The boxed machine.}
The entire construction can be stated in a single pipeline:
\[
\boxed{
\text{homotopy chiral input }\cA
\;+\;
\text{log-FM cutting cooperad }\mathcal C^!_{\mathrm{ch}}
\;+\;
\text{modular convolution }L_\infty
\;\;\Longrightarrow\;\;
\Theta_\cA,\;
\mathcal T^{\mathrm{mod}}_{\Theta_\cA},\;
\kappa,\;
\Delta_\cA,\;
\mathfrak R^{\mathrm{mod}}_4,\;\ldots
}
\]

\noindent
The modular convolution $L_\infty$-algebra
$\gAmod$ is the single organising structure.
It carries a natural modular $L_\infty$ structure from the Feynman
transform of the modular operad; the dg Lie algebra
$\operatorname{Conv}_{\mathrm{str}}(\mathcal C^!_{\mathrm{ch}},
\mathcal P^{\mathrm{ch}})$ is its strict model.  The universal MC
element
$\Theta_\cA\in\MC(\gAmod)$,
satisfying
\[
D\cdot\Theta_\cA+\tfrac12[\Theta_\cA,\Theta_\cA]\;=\;0,
\]
is proved: it is the bar-intrinsic extraction
$\Theta_\cA:=D_\cA-d_0$, which is MC because $D_\cA^2=0$.

The shadow obstruction tower consists of finite-order projections:
\begin{align*}
\Theta_\cA^{\le 2}&:\qquad\kappa(\cA)
  &&\text{(modular characteristic, scalar curvature)},\\
\Theta_\cA^{\le 3}&:\qquad\mathfrak C(\cA)
  &&\text{(cubic shadow, Lie structure)},\\
\Theta_\cA^{\le 4}&:\qquad\mathfrak Q(\cA)
  &&\text{(quartic resonance class, contact structure)},\\
\Theta_\cA^{\le r}&:\qquad\operatorname{Sh}_r(\cA)
  &&\text{(arity-$r$ shadow)},\\
\Theta_\cA&:\qquad\varprojlim_r\Theta_\cA^{\le r}
  &&\text{(the universal MC element)}.
\end{align*}
Theorems~A--D+H and the genus expansion are proved projections
of the scalar level~$\kappa$.  The holographic datum
$\mathcal H(T)=(\cA,\cA^!,\cC,r(z),\Theta_\cA,\nabla^{\mathrm{hol}})$
packages $\Theta_\cA$ and its projections into the data of a 3d
holomorphic-topological field theory.

\bigskip

\noindent\textbf{The computational infrastructure.}
Every formula in this preface has been verified by an independent symbolic
computation layer comprising tens of thousands of tests across several
hundred modules, covering the shadow obstruction tower through arity~$32$,
the standard landscape for all seven families, and the genus-$2$ and
genus-$3$ planted-forest formulas.  The computation is adversarial: tests
encode cross-family consistency checks (additivity, complementarity,
anti-symmetry) that cannot be fooled by a single hardcoded value.

\begin{principle}[The four-test interface]
\label{princ:four-test-interface}
\index{four-test interface|textbf}%
The modular Koszul machine has a complete algebraic-geometric
interface with $\overline{\mathcal M}_{g,n}$, consisting of
four independent proved tests:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item $D_\cA^2 = 0$:
  the bar differential squares to zero at all genera and arities
  \textup{(}Theorems~\textup{\ref{thm:bar-modular-operad},
  \ref{thm:quantum-diff-squares-zero}}\textup{)}.
\item $\mathrm{obs}_g(\cA) = \kappa(\cA)\cdot\lambda_g$
  for uniform-weight algebras at all genera,
  and unconditionally at genus~$1$ for all families
  \textup{(}Theorem~\textup{\ref{thm:modular-characteristic}}\textup{)}.
\item $Q_g(\cA)+Q_g(\cA^!)=H^*(\overline{\mathcal M}_g,Z(\cA))$:
  complementarity assembles the Koszul pair into a Lagrangian
  decomposition
  \textup{(}Theorem~\textup{\ref{thm:quantum-complementarity-main}}\textup{)}.
\item Sewing:
  genus-$g$ amplitudes converge from lower-genus data
  \textup{(}Theorem~\textup{\ref{thm:general-hs-sewing}}\textup{)}.
\end{enumerate}
\end{principle}

\bigskip

\noindent\textbf{The single open problem.}
Everything proved in this monograph is a finite-order projection
of the universal MC element
$\Theta_\cA \in \MC(\gAmod)$.
Everything open is a question about its ambient:

\begin{center}
\fbox{\parbox{0.85\textwidth}{\centering
\emph{Characterise the modular convolution algebra
$\gAmod$ as a geometric object.}
}}
\end{center}

\noindent
Precisely: the modular convolution algebra is the endomorphism
algebra of the Lagrangian embedding
$\cL_\cA \hookrightarrow \cM_{\mathrm{vac}}(\cA)$ in the
$(-2)$-shifted symplectic stack of vacua.  Volume~I computes
the Taylor jets of this embedding (the shadow obstruction tower).
Volume~II identifies the local composition law (the Swiss-cheese
operad).  What remains is the global geometry of the stack itself:
the derived symplectic structure, the moduli of Lagrangians, and
the higher-categorical descent that would make the construction
independent of choices.

The open conjectures in these two volumes are projections
of this single question:
\begin{itemize}[nosep]
\item the D-module purity conjecture asks whether the Lagrangian
  is pure (characterisation (xii) of Koszulness);
\item the non-principal W-duality programme asks how the Lagrangian
  transforms under Drinfeld--Sokolov reduction at arbitrary
  nilpotent orbits;
\item the analytic completion programme asks when the algebraic
  Lagrangian extends to a convergent one (the sewing envelope);
\item the factorization envelope programme asks for the universal
  construction of the Lagrangian from Lie conformal data alone;
\item the holographic completion question asks whether the genus-$0$
  Lagrangian extends over $\overline{\cM}_{g,n}$ (the modular
  programme of Volume~II);
\item the Calabi--Yau quantum group programme asks whether the
  automorphic correction of a generalized Borcherds--Kac--Moody
  superalgebra is the shadow obstruction tower of an $E_2$-chiral
  algebra constructed from a CY category (proved for $d=2$;
  conditional on chain-level $\mathbb S^3$-framing for $d=3$;
  Volume~III).
\end{itemize}
Each is a different facet of the geometry of
$\gAmod$, and none requires going
beyond the framework already established.

\bigskip

\noindent
The entire structure unfolds from a single datum: the logarithmic
$1$-form $\eta = d\log(z_1 - z_2)$.  At $n$~points, $\eta$ generates a
differential on the Fulton--MacPherson compactification.  Across all
genera, it generates the total bar differential~$D_\cA$.  In the modular
convolution algebra, it generates the Maurer--Cartan element
$\Theta_\cA = D_\cA - d_0$.  One $1$-form, one relation (Arnold),
one extraction (residues): a universal invariant of chiral algebras
that is algebraic, computable, and complete.
