% =====================================================================
%
% PROGRAMME OVERVIEW -- PLATONIC INSCRIPTION
%
% Three volumes, five main theorems, and the auxiliary reconstruction
% and classification surfaces that sit downstream of them.
% Russian-school prose: construct, do not narrate.
%
% Location in the monograph: immediately after the preface, before the
% Introduction and the Overture. The reader who has finished the
% preface meets here the global skeleton in the form governed by the
% concordance.
%
% =====================================================================

\providecommand{\ChirHoch}{\operatorname{ChirHoch}}
\providecommand{\ChirAlg}{\operatorname{ChirAlg}}
\providecommand{\HTQFT}{\operatorname{HT\text{-}QFT}}
\providecommand{\Phihol}{\Phi_{\mathrm{hol}}}
\providecommand{\Face}{\operatorname{Face}}
\providecommand{\GRTone}{\operatorname{GRT}_1}
\providecommand{\kcat}{\kappa_{\mathrm{cat}}}
\providecommand{\kch}{\kappa_{\mathrm{ch}}}
\providecommand{\kBKM}{\kappa_{\mathrm{BKM}}}
\providecommand{\kfib}{\kappa_{\mathrm{fiber}}}
\providecommand{\SCchtopan}{\mathsf{SC}^{\mathrm{ch,top,an}}}

\chapter*{Programme Overview}
\addcontentsline{toc}{chapter}{Programme Overview}
\label{ch:programme-overview-platonic}
\markboth{Programme Overview}{Programme Overview}

\vspace{1em}

\section*{1.\quad The shadow of a 4d HT gauge theory}
% =====================================

\noindent
A 4d holomorphic-topological gauge theory on $\bC\times\bR_{\ge 0}$
with a Dirichlet boundary condition at the origin of~$\bR_{\ge 0}$
descends to a 2d chiral algebra~$\cA$ on the curve~$\bC$. The algebra
is concrete: its state space is the space of boundary local
operators, its OPE is the collision limit of the 4d-to-boundary
restriction, and its modular structure is the residual action of the
2d conformal group preserved by the boundary. The 4d theory admits
multiple dualities and redefinitions; the algebra~$\cA$ is a
boundary shadow, coarser than the 4d theory but finer than any
isolated numerical invariant. A census of the families that arise
(Heisenberg, affine Kac--Moody at level~$k$,~$\beta\gamma$, Virasoro,
principal~$W_N$, their orbifolds and extensions) is performed in
the standard-landscape part. For any such~$\cA$ the Infinite Fingerprint classification
(Chapter~\ref{chap:infinite-fingerprint-classification}) extracts
the six-slot invariant
\[
 \phi'(\cA) \;=\;
 \bigl(\,p_{\max},\;r_{\max},\;\chi_{\mathrm{VOA}},\;
 n_{\mathrm{strong}},\;\mathrm{coset},\;\kch\,\bigr),
\]
where $p_{\max}$ is the maximal OPE-pole order, $r_{\max}$ is the
shadow-tower depth, $\chi_{\mathrm{VOA}}$ is the supertrace
character, $n_{\mathrm{strong}}$ is the strong-generator count,
$\mathrm{coset}$ is the automorphism coset, and $\kch$ is the
central-extension class pulled back from the Theorem-D universal
Arakelov class. Theorem~G below proves that $\phi'$ is complete on
the standard landscape; the five-class $G/L/C/M/FF$
projection is its double coarsening, first forgetting $\kch$ then
projecting onto $r_{\max}$ (with the $\kch=0$ stratum forming the
Feigin--Frenkel class $FF$).

The fingerprint is computable, useful, and lossy. It collapses the
action of the Grothendieck--Teichm{\"u}ller group~$\GRTone(\bQ)$ on
the face lattice~$\Face(\cA)$ of the bar complex to a~$\bQ$-rational
quotient; the associator-level and spectral-level data invisible to
the numerical census survive in the ordered bar package itself. The
shadow-depth projection is
$\mathsf G/\mathsf L/\mathsf C/\mathsf M/
\mathsf M^{\mathrm{ext}}/\mathsf B$; the Feigin--Frenkel critical
stratum is a companion boundary where Sugawara degenerates, not an
additional archetype. The five theorem packages of Section~2 record
the invariant content that
survives the averaging map: the bar-cobar arena, inversion,
complementarity, scalar genus class, and chiral Hochschild coefficient
ring. Holography and fingerprint completeness are downstream
architectural surfaces; they organize reconstruction and
classification after the five-theorem spine is in place.

\section*{2.\quad Five theorem packages}
% =====================================

\noindent
Five theorem packages stratify the invariant content of~$\cA$.
Each is stated on the exact proved surface used by the concordance;
ambient qualifications are part of the theorem hypotheses, not a
separate status layer.

\medskip

\noindent\textbf{Theorem~A$^{\infty,2}$ (Bar-cobar properad
adjunction).}\enspace
The ordered bar construction
$\barB^{\mathrm{ord}}_X(\cA) = T^c(s^{-1}\bar\cA)$
and its cobar $\Omega_X$ are load-bearing in two lanes. On the chain
lane they form the bar-cobar adjunction with universal twisting
morphism and counit witness, whose Verdier image identifies the
post-dual bar with the factorization algebra~$\cA^{!}_\infty$.
On the factorization-$\infty$ lane the same package lifts to the
Francis--Gaitsgory/Lurie adjunction on $\Ran(X)$ with
$R$-twisted $\Sigma_n$-descent. The theorem read out in the Climax
chapter is therefore simultaneously chain-level and
$(\infty,1)$-categorical; neither lane is a shadow of the other.

\medskip

\noindent\textbf{Theorem~B (Bar-cobar inversion on the Koszul
locus).}\enspace
On the Koszul locus the counit
$\Omega_X(\barB_X(\cA))\xrightarrow{\sim}\cA$ is a
quasi-isomorphism. Off the strict lane, the explicit
weight-completed chiral CDG-coalgebra
$\widehat{C}=\widehat{\barB}^{\mathrm{ch}}(\cA)$ carries the chiral
Positselski equivalence in the coderived/contraderived ambient of
holonomic factorization $\mathcal{D}$-modules on~$X$
\textup{(}Theorem~\ref{thm:chiral-positselski-7-2}\textup{)}.
This does \emph{not} mean the raw direct-sum bar complex is acyclic in
class~$M$: there the quartic obstruction
$S_4(\mathrm{Vir}_c)=10/[c(5c+22)]$ forces genuine failure, so the
restored statement is weight-completed / pro-object / $J$-adic, not
raw direct sum.

The same ordered bar package carries the universal conductor of
Chapter~\ref{chap:universal-conductor}: the Reynolds/coinvariant
averaging from ordered chiral homology to the symmetric modular
shadow. Its kernel is the ordered residue sector detected by the
$G/L/C/M$ archetypes, and it is separate from both the derived centre
and the categorical Drinfeld centre.

\medskip

\noindent\textbf{Theorem~C ($-(3g{-}3{+}n)$-shifted symplectic
structure with Lagrangian section).}\enspace
The chiral derived centre
$\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA) = \ChirHoch^\bullet(\cA,\cA)
= \operatorname{RHom}_{\End^{\mathrm{ch}}_{\cA}}(\cA,\cA)$
(chiral Hochschild with spectral parameters in
$\End^{\mathrm{ch}}_\cA$, distinct from topological and categorical
Hochschild) has a proved C0/C1 core: the Verdier eigenspace
decomposition and Lagrangian duality of the derived centre. The
shifted-symplectic BV theorem is the C2 surface on the BV-perfect,
Verdier-nondegenerate bar-chart locus, including the verified
Heisenberg and affine-Kac--Moody perfectness surface. On the classical
$\mathsf G/\mathsf L/\mathsf C/\mathsf M$ census families the
restricted scalar Verdier sums are
$0$ for Heisenberg, affine Kac--Moody, and $\beta\gamma/bc$,
$13$ for Virasoro, $250/3$ for~$\mathcal{W}_3$, and $98/3$ for
Bershadsky--Polyakov. The Vol~III $\mathsf B$-row adds the canonical
fifth bucket value $8$ through the Mukai-enhanced K3 Heisenberg
witness.

\medskip

\noindent\textbf{Theorem~D (Tensor curvature on the Arakelov
class).}\enspace
On~$\overline{\cM}_{g,n}$, the free-energy package is
\[
 F_g(\cA)
 \;=\;
 \kappa(\cA)\cdot\lambda_g^{\mathrm{FP}}
 \;+\;
 \delta F_g^{\mathrm{cross}}(\cA)
 \qquad\textup{(ALL-WEIGHT $+\delta F_g^{\mathrm{cross}}$)},
\]
with $\delta F_1^{\mathrm{cross}}=0$ universally and
$\delta F_g^{\mathrm{cross}}=0$ on the uniform-weight lane, where
the cohomological obstruction class becomes
$\operatorname{obs}_g(\cA)=\kappa(\cA)\cdot\lambda_g$ with
$\lambda_g = c_g(\mathbb{E})$ the top Chern class of the Hodge
bundle. The proof is the
Bismut--Gillet--Soul\'e fiberwise Chern-curvature formula in
Arakelov metric, lifted from $c_1$ to $c_g$ of the full Hodge bundle
by the splitting principle together with scalar-channel linearity of
the bar curvature. Off the uniform-weight lane at~$g\ge 2$ the
correction~$\delta F_g^{\mathrm{cross}}$ is explicit; for~$W_3$ at
genus~$2$ it reads
$\delta F_2^{\mathrm{cross}}(W_3) = (c+204)/(16c)$
(Theorem~\ref{thm:delta-f-cross-w3-g2}).
The clutching-only residue is
Conjecture~\ref{conj:F6-lambda-g-clutching-uniqueness},
which asks for the socle equality to lift to on-the-nose equality in
$R^g(\overline{\cM}_g)$ at $g\ge3$.

\medskip

\noindent\textbf{Theorem~H (Chiral Hochschild concentration).}\enspace
This is the \emph{chiral} Hochschild theory
$\ChirHoch^\bullet(\cA)=C^\bullet_{\mathrm{ch}}(\cA,\cA)$, distinct
from topological $\mathrm{THH}$ and categorical
$\mathrm{HH}_{\mathrm{cat}}^\bullet$. On the Koszul locus, and in
particular on the generic-level class-$G/L/C/M$ surfaces recorded in
the concordance, it has cohomological amplitude~$[0,2]$ together with
the derived duality shift~$[2]$. The Hilbert series
takes the sharp form
\[
 P(t,q) \;=\;
 \mathrm{HS}_{Z(\cA)}(q) + \mathrm{HS}_{\ChirHoch^1(\cA)}(q)\cdot t
 + \mathrm{HS}_{Z(\cA^{!})}(q)\cdot t^2.
\]
Critical affine level and non-generic class~$M$ parameters sit outside
this proved surface. The Swiss-cheese package belongs to the pair
$(C^\bullet_{\mathrm{ch}}(\cA,\cA),\cA)$; the bar coalgebra itself
remains an $E_1$-coalgebra.

\medskip

Two auxiliary theorem surfaces sit downstream from the five invariant
packages. They are not extra main theorems of Volume~I; they organize
reconstruction and classification once the bar-cobar spine has been
fixed.

\medskip

\noindent\textbf{Theorem~F (Universal Holography).}\enspace
Let~$\ChirAlg^{\omega,\mathrm{BL},\mathrm{nonlog}}_X$ denote the
category of conilpotent boundary-Lagrangian chiral algebras on the
curve~$X$ in the \emph{non-logarithmic} standard landscape
(Virasoro, $W_N$ for any~$N$, Schellekens $c=24$ holomorphic,
Monster~$V^{\natural}$, irrational cosets), and
let~$\HTQFT_{X\times\bR}$ denote the category of
holomorphic-topological quantum field theories
on~$X\times\bR$ with an anchored boundary condition. The assignment
\[
 \Phihol\colon\;
 \ChirAlg^{\omega,\mathrm{BL},\mathrm{nonlog}}_X
 \;\longrightarrow\;
 \HTQFT_{X\times\bR},
 \qquad
 \cA \;\longmapsto\;
 \bigl(\,\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cA)
 \;\rightsquigarrow\;
 (\cA,\cA^{!}_\infty)\,\bigr)
\]
is the typed open/closed comparison functor under the
Volume~II non-logarithmic hypotheses.  Its algebraic input is not the
bar-cobar pair alone: bar-cobar inversion recovers the boundary
algebra~$\cA$, Verdier duality supplies the homotopy Koszul partner
$\cA^!_\infty$, and the chiral derived center supplies the
cochain-level closed-sector slot.  The physical HT bulk-boundary pair is
obtained only after the Vol~II comparison functor identifies that
open/closed package with a holomorphic-topological field theory.
The functor is constructed in
Chapter~\ref{chap:universal-holography-functor} of Volume~II with the
\emph{non-logarithmic} scope qualifier. The logarithmic~$\cW(p)$
triplet is excluded at the current scope; Gurarie-Flohr unbounded
Massey amplitudes refute the Zhu-bounded-Massey argument used for its
tempering. The remaining route for~$\cW(p)$ is a direct
Adamovi\'c-Milas character-amplitude bound. The Vol.~II comparison
theorem applies on the non-logarithmic $C_2$-cofinite standard
landscape plus irrational cosets in that ambient.
The stratification refines to the \emph{shadow-exponential base}
invariant~$C_\cA = r_0 \cdot S_{r_0}(\cA)$: on the non-logarithmic
class M standard landscape, $C_\cA = 6$ uniformly, and the shadow
series~$\Sigma_\cA(z)$ has radius of convergence~$1/6$ with a
logarithmic branch point at~$z = -1/6$ (Virasoro closed form
$\Sigma_\Vir(z) = 4 z^3/9 - z^2/9 + z/27 - \log(1+6z)/162$,
Theorems~\ref{thm:shadow-exponential-base-Virasoro},
\ref{thm:universal-class-M-C-is-6},
\ref{thm:shadow-series-closed-form-Virasoro} in
Chapter~\ref{ch:shadow-tower-higher-coefficients}). The
$(\infty, 2)$-adjoint equivalence holds uniformly on the
$C_\cA = 6$ stratum; the $(\infty, 1)$-adjoint morphism on the
logarithmic~$\cW(p)$ stratum is obstructed at the
$(\infty, 2)$-upgrade by the Gurarie-Flohr Massey class.

\medskip

\noindent\textbf{Paramodular refinement of Theorem~F.}\enspace
At the K3 base, Theorem~F acquires a paramodular quadrichotomy
refining the shadow-depth quadrichotomy. The master K3 chiral
bialgebra
$\mathbf H_{\Delta_5}
=\mathrm{Borch}(F_3,\phi^{K3}_{0,1})$
on the hyperbolic lattice $\Lambda_{\mathrm{Muk},II}^{2,1}$
produces four sibling functors
$\{\Psi,\Psi^{\deg},\Psi^{\mathrm{tor}},\Psi^{\mathrm{metap}}\}$
indexed by the Baily--Borel--Freitag stratification of
$\overline{\mathcal A_2}$: the reflective interior, the Klingen
cusp (super-affine), the Humbert divisor (quantum-toroidal), and
the metaplectic branch (Conway $V^{s\natural}$). The
genus-$1$ free energy of $\mathbf H_{\Delta_5}$ is the master
Quillen--Arakelov $L$-value identity
\[
\log Z^{(1)}_{\mathbf H_{\Delta_5}}
\;=\;-\log\bigl\|\Delta_5\bigr\|^2_{\mathrm{Quillen}}
\;=\;-\log\Delta_5 \;-\; 24\cdot L'(0,\Delta_5,\mathrm{std}),
\]
where $\Delta_5 \in S_5(K(1))$ is the Gritsenko paramodular
weight-$5$ cusp form and $24 = \chi_{\mathrm{top}}(K3)$ is the
Bismut--Gillet--Soul\'e coefficient (Bruinier--K\"uhn 2003 +
Bismut--Gillet--Soul\'e 1988); the standard $L$-function replaces
adjoint-spinor candidates via Pitale--Saha--Schmidt 2014 CAP
factorisation and the Waldspurger squaring rule. The Humbert wall
is the Argyres--Douglas locus of the class-$\mathcal S$ SCFT
$\mathcal T[A_1,\Sigma_{0,24}]$: at $E_{\tau_1}\times E_{\tau_2}$
the Seiberg--Witten curve degenerates to $(A_1,A_{2N-1})$
(Gaiotto--Moore--Neitzke 2009, Example~8.3). Inscribed at
Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.

\medskip

\noindent\textbf{Theorem~G (Infinite Fingerprint Completeness).}\enspace
On the standard landscape, the six-slot fingerprint~$\phi'(\cA)$ is
a complete invariant of the bar coalgebra together with its Koszul
dual: $\phi'(\cA_1) = \phi'(\cA_2)$ if and only if
$\barB^{\mathrm{ch}}(\cA_1)\cong\barB^{\mathrm{ch}}(\cA_2)$ as
$\operatorname{Ass}^{\mathrm{ch}}$-coalgebras and
$\cA_1^{!}\cong\cA_2^{!}$. The quadrichotomy~$G/L/C/M$ is recovered
as the first coarse projection~$\Pi_{\mathrm{coarse}}\circ\phi'$,
forgetting $\kch$ and projecting onto $r_{\max}$, on the
locus~$\kch\ne 0$. The critical-level companion stratum~$FF$
($\kch = 0$) completes the classification to the five-class
$G/L/C/M/FF$. The theorem is proved in
Chapter~\ref{chap:infinite-fingerprint-classification}.

\section*{3.\quad The volume}
% =====================================

\noindent
The volume has an overture, six numbered parts, and appendices. The
order follows mathematical dependence: first the object, then its
scalar and nonlinear shadows, then examples, physics bridges,
collision residues, and the frontier boundary.

\medskip

\noindent\textbf{Overture.}\enspace
The Heisenberg algebra exposes the ordered bar in the abelian base
case: one generator, one double pole, one scalar~$k$.

\medskip

\noindent\textbf{Foundations and the Open Beilinson Tower.}\enspace
Levels $0$--$1$: introduces the tangential log curve
$(X, D, \tau)$, the factorisation dg-category $\cC^{\op}$, the
chosen vacuum $b \in \cC^{\op}$, and the chart algebra
$A_b = \End_\cC(b)$. Recalls classical Koszul duality and the
configuration-space geometry on which the bar differential will be
defined. Heisenberg overture in the abelian base case.

\medskip

\noindent\textbf{The Bar--Cobar Engine.}\enspace
Constructs $\Bbarch_X(A_b) = \mathrm{T}^c(s^{-1}\bar A_b)$ at
level~$2$ and proves Theorem~A in parametric strength: bar--cobar
adjunction unconditional; counit $\Omega B(A_b) \xrightarrow{\sim}
A_b$ a chain-level quasi-isomorphism on $\Kosz(X)$; off-locus
strongest reading rejected, replaced by Theorem~H. The chain-homotopy
norm $\mathcal N(A_b)$ inverts the universal Loday--Vallette
contraction. The shadow tower $\{S_2, S_3, S_4, \dots\}$ exposes the
fingerprint of $A_b$.

\medskip

\noindent\textbf{The Bulk.}\enspace
Theorem~H (Hochschild concentration $\subset \{0,1,2\}$ on the
Koszul locus) and Theorem~B (strict bar--cobar inversion on
Koszul, weight-completed Positselski lane off it) identify the
derived chiral centre $Z^{\mathrm{der}}_{\mathrm{ch}}(A_b)$ at
level~$3$ as the genuine bulk. The five-object firewall keeps the
bar coalgebra at level~$2$ distinct from the bulk at level~$3$
(Master Pattern MA-4).

\medskip

\noindent\textbf{The Five-Archetype Landscape.}\enspace
Stratifies the standard landscape (Heisenberg, affine Kac--Moody at
level~$k$, $\beta\gamma$, $bc$, Virasoro, principal $\cW_N$,
non-principal $\cW$ of hook type, logarithmic $W(p)$, symplectic
bosons and fermions, super-Virasoro, Bershadsky--Polyakov, lattice
VOAs, Mukai-K3 Heisenberg) into the five archetypes
$\mathsf G / \mathsf L / \mathsf C / \mathsf M / \mathsf B$ via the
$5{\times}5$ $\kappa$-stratification matrix; K3$\times E$ anchors
row $\mathsf B$ at $(0, 0, 3, 5, 24)$.

\medskip

\noindent\textbf{The Modular Tower.}\enspace
Levels~$4$--$5$: line/brane operators, modular trace, and clutching
on the open category. Theorem~D
$\mathrm{obs}_g(A_b) = \kappa(A_b) \cdot \lambda_g$ on the
uniform-weight scalar lane; Borel--Riccati shadow tower
$|\omega|^2(c) = c^2(5c+22)/[4(45c+218)]$ as the modular spine.
The physics-bridge witnesses (Feynman diagrams, BV-BRST, arithmetic
shadows) realise $\mathrm{obs}_g$ in concrete computations. The
$E_n$ operadic circle $E_3 \to E_2 \to E_1 \to E_2 \to E_3$, the
factorization-envelope construction $\cU^{\mathrm{mod}}_X$, the
derived-Langlands mirror, and the Dimofte slab as a bimodule
inscribe at the modular tower's higher-categorical level.

\medskip

\noindent\textbf{Seven Faces of $r_\cA(z)$.}\enspace
Treats the family-normalized collision residue across its seven faces:
for example $r^{\mathrm{Heis}}_k(z)$, $r^{KM,\fg}_k(z)$, and
$r^{\mathrm{Vir}}_c(z)$. The seven faces are F1
bar-cobar twisting, F2 DNP25 line-operator, F3 Khan--Zeng
PVA, F4 Gaiotto--Zeng sphere Hamiltonians, F5 Drinfeld Yangian, F6
Sklyanin, F7 FFR94 Gaudin. The~$\GRTone(\bQ)$-torsor acts on the
face lattice and the seven faces are its pinned points.

\medskip

\noindent\textbf{Frontier.}\enspace
The boundary of the proved surface: critical level, logarithmic
admissible families, super-Yangian Berezinian shifts, and
cross-volume CY-to-chiral shadows.

\medskip

\noindent\textbf{Appendices.}\enspace
Census tables, first-principles diagnostics, operadic conventions, and
computational tables.

\medskip

Former frontier questions are recorded in the Guide to Main Results
and in the concordance with their exact status: proved surfaces,
ambient-qualified completions, reductions, and residual conjectures
are not collapsed into a single slogan.

\section*{4.\quad Three volumes}
% =====================================

\noindent
The programme consists of three volumes.

\medskip

\noindent\textbf{Volume~I.\ Modular Koszul Duality.}\enspace
The algebraic spine: ordered bar complex, five-theorem core,
standard landscape, physics bridges, and seven faces of the
family-normalized collision residue~$r_\cA(z)$.

\medskip

\noindent\textbf{Volume~II.\ A-$\infty$ Chiral Algebras and 3d HT
QFT.}\enspace
The physical realization. Opens with the open-primitive atom,
develops the~$E_1$ core, installs the
$\SCchtopan$ derived-centre pair computed by the bar-resolution shadow,
and treats the 3d quantum-gravity value on its Brown--Henneaux/HT-QFT
scope.

\medskip

\noindent\textbf{Volume~III.\ CY Categories, Quantum Groups, and BPS
Algebras.}\enspace
The geometric realization. Constructs the CY-to-chiral two-stage
factorisation
$\Phi_d = \mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1}, C} \circ
\Phi^{\mathrm{FA}}_d$ -- stage~$1$ a canonical $E_d$-holomorphic
factorisation algebra on the CY$_d$ variety (pinned by
Kontsevich--Tamarkin $E_d$-formality and Costello--Gwilliam--Li
locality), stage~$2$ factorisation homology over a closed
$(d-1)$-cycle $\Sigma_{d-1}$ followed by restriction to a reference
curve $C$ -- scope-dependent on the complex dimension~$d$ (an
$E_2$-chiral output on $C$ for $d\le 2$; an $E_1$-chiral output on
$C$ for $d\ge 3$, with a family of $E_1$-chiral shadows indexed by
$(\Sigma_{d-1}, C)$), the K3~Yangian,
the BKM conductor~$\kBKM = c_N(0)/2$, and the class-$M$ $E_3$ bar of
dimension~$6^g$ at $g\in\{1,2,3\}$, with the $g\ge 4$ extension
belonging to the $d_5$-degeneration surface of
Volume~III \ref{V3-cor:class-m-higher-genus}.
On the current honest surface, CY-D proves the $d=2$,
$\HH_{-1}=0$ slice and then separates the operational
$\kappa_{\mathrm{ch}}$ from the Hodge comparator
$\chi(\cO_X)$ beyond that slice; K3 categorical DT proves the
Hilbert-scheme Fock bridge. The proved statement used here is that
Fock bridge, not a bar-side categorical lift to
$D^b(\Hilb^n(K3))$.

\section*{5.\quad The Platonic endpoint}
% =====================================

\noindent
The operadic circle
$\cdots\to E_{n+1}\to E_n\to\cdots\to E_1\to E_2\to\cdots\to E_{n+1}\to\cdots$
closes at~$E_\infty$-topological as the formal completion of both
arms. The inward arm collapses the topological directions one at a
time; the outward arm unfolds the holomorphic directions one at a
time through iterated derived-centre constructions. At each rung~$n$
the conformal vector on the~$n$-th Sugawara level is the data that
makes the~$\bC$-translations~$Q$-exact and promotes~$\SCchtopan$
to~$E_{n+1}^{\mathrm{top}}$. Iterating the Sugawara construction
produces the~$W_\infty$ tower; its~$N\to\infty$ limit is~$E_\infty$.
The first visible shadow of the endpoint is 3d quantum gravity at
the~$W_\infty$ level of Volume~II, Part~VI. The programme does not
construct~$E_\infty$ directly: it constructs the~$W_\infty$ tower
and identifies its formal completion with the endpoint.

The endpoint is Platonic in a precise sense: it is the unique
operadic fixed point of the iterated Sugawara construction on the
tower of chiral algebras with conformal vector at non-critical
level. On the standard landscape it exists. Off the standard
landscape (the degenerate lane, the critical level, the logarithmic
regime of Creutzig--Kanade--Linshaw) the fixed point is the active
frontier.

\section*{6.\quad The non-degenerate surface}
% =====================================

\noindent
On the non-degenerate locus
$\{\,\kch\ne 0,\;\text{non-critical level},\;\text{Koszul locus}\,\}$,
the five main theorem packages have the status recorded in the
concordance: A, B, D, and H are proved on their stated surfaces; C has
proved C0/C1 clauses and a C2 shifted-symplectic theorem on the
BV-perfect, Verdier-nondegenerate bar-chart locus.
The auxiliary holography and fingerprint surfaces use this spine; they
do not replace it. Off the non-degenerate locus the critical affine
stratum, logarithmic admissible lane, super-Yangian Berezinian shift,
and CY-to-chiral higher-dimensional shadows are separate theorem
surfaces with their own hypotheses.

\section*{7.\quad The residual boundary}
% =====================================

\noindent
The active frontier is the residual boundary of the non-degenerate
locus. Four pieces.

\medskip

\noindent\emph{(a) The degenerate admissible logarithmic
lane.}\enspace
The Creutzig--Kanade--Linshaw logarithmic VOAs~$W(p)$ and their
relatives occupy a specific stratum of the standard landscape on
which the Koszul locus is obstructed by a Massey triple product
$\langle\Omega,\Omega,\Omega\rangle$ at weight~$3$. Gurarie 1993 and
Flohr 1996 exhibit unbounded Massey amplitudes at every weight
for~$\cW(p)$, which refutes the Zhu-bounded-Massey shortcut used
for temperedness; direct Adamovi\'c--Milas character-amplitude bounds
remain the residual route. The stratum is explicit and its scope is
delimited.

\medskip

\noindent\emph{(b) The Volume~III CY-C six-routes
convergence.}\enspace
The six routes to the K3 chiral algebra are read on their
route-specific proof surfaces. The Borcherds-lift and lattice-VOA
route is ProvedElsewhere, and the remaining bridges are not used as
global theorem inputs in this overview. The pentagon stratifies the
generator-lattice rank~$\rho^{R_i}\in\{3,12,24\}$, NOT the Hodge
supertrace~$\kch$ (which is route-independent and vanishes on
$K3\times E$); the halving arrows~$\beta_{34}$,~$\beta_{45}$ act on
$\rho$ alone. The frontier is stated at its proved strength; no
bridge is misreported.

\medskip

\noindent\emph{(c) The paramodular arithmetic frontier.}\enspace
The master K3 chiral bialgebra $\mathbf H_{\Delta_5}$ carries a
one-dimensional Bloch--Kato Selmer deformation
$\dim H^1_f(\mathbb Q,\mathrm{std}\,\rho_{\Delta_5}) = 1$, the
paramodular cyclotomic Hida-family tangent. The
metaplectic Grothendieck--Teichm\"uller extension
$\mathrm{grt}_1^{(1/2)}$ of $\mathrm{grt}_1$ by even-weight
generators, with fundamental bracket
$[\widetilde\sigma_2,\widetilde\sigma_2] = 288\,\widetilde\sigma_4$
and $288 = \tau(2)^2/2$, acts on the Saito--Kurokawa motivic
shadow. The chiral-Hochschild $W_\infty[c=-214]$ cocycles
$e_3,e_4,e_5,e_6$ are explicit: $e_5 = W_5$ identically (Wang 1998,
Proposition~4.2), and $e_4 = W_4 - (107/11)\Lambda_Z$. The
Humbert--Heegner admissibility filtration
$\phi^{(n)}=0$ unless $n\equiv 3,5\pmod 8$ separates the K3
polar-support lane from Zagier--Hoffman regularisation. The $H_3$
wall carries $\phi^{(3)}|_{H_3}$, the one-term $n=5$ coherence is
$\phi^{(5)} = 2\,[\mathrm{gen}]^{\otimes 5}$ in the normalization of
Theorem~\ref{thm:bc-unconditional-depth-reduction}, and the polar
coefficient vanishes for admissible $n\ge 11$. These
arithmetic data are the K3-base deformation theory of the holography
surface, proved in Chapter~\ref{V3-ch:k3-chiral-bialgebra-platonic}.

\medskip

\noindent\emph{(d) The super-Yangian chain-level chiral
coproduct.}\enspace
The super-Yangian complementarity question separates into the
proved super-trace identity used here and a separate Berezinian-shift
surface. The
super-trace normalisation gives
$\kappa^{\str} + \kappa^{\str,!} = 0$ on the sub-Sugawara line
for $\fsl(m|n)$ with $m\neq n$
(Proposition~\ref{prop:super-berezinian-central-automorphism}(a),
proved via super-Sugawara rational-identity cancellation). The
Berezinian normalisation is formulated separately as
$\kappa^{\sBer} + \kappa^{\sBer,!} = \max(m,n)$
(Conjecture~\ref{conj:super-berezinian-shadow-shift-magnitude}),
with the required closed-form derivation of the shift magnitude
$\tfrac{1}{2}\max(m,n)$ induced by the central automorphism
$\sigma_{\sBer}$ of
Lemma~\ref{lem:super-trace-berezinian-bridge}; Nazarov~1991 and
Gow~2006 supply centrality of $\sBer(T(u))$ and non-degeneracy of
the Berezinian pairing, but not the shift magnitude in closed
form (Remark~\ref{rem:super-berezinian-shift-open}). The Verdier pairing specialises
to super-trace on supertraceless type-$A$; the Sugawara pairing
specialises to Berezinian. Neither normalisation is more
canonical than the other; the complementarity datum is
invariantly defined on $Z(A) \otimes Z(A^{!})$ and both recover
it.

\medskip

\noindent
The skeleton is three volumes, five main theorem packages, and
auxiliary reconstruction/classification surfaces. The non-degenerate
surface is not advertised as complete by enumeration; it is bounded by
the four frontier pieces above and by the concordance.

\medskip

\noindent\textbf{Architectural sharpenings.}\enspace
The programme-level statements refine into the forms in which the
theorems are proved.

\emph{Four conductors, trinity restricted.} The single conductor
$K$ of equation~(G1) separates into $K$ (BRST ghost conductor),
$K^\kappa := \kappa+\kappa^!$ (complementarity ceiling, values
$(0,13,250/3,98/3,8)$ on $(\mathsf G,\mathsf L,\mathsf C,\mathsf M,\mathsf B)$),
$K_c$ (central-charge trace), and $K_g$ (ghost-number anomaly). The
trinity $K=K_c=K_g$ coincides only on the Koszul-self-dual subcategory
admitting BRST resolution and Borcherds-CY target.

\emph{Universal chain-homotopy normalisation.} For each chirally
Koszul $\cA$ the contracting homotopy on $K^2(\cA)\simeq\cA$ is
$h_\cA = h_{\mathrm{LV}}/(\kappa+\kappa^!)$; the complementarity
ceiling is the chain-level bridge from Theorem~A to Theorem~C.

\emph{Two-stage Calabi--Yau factorisation.} The cross-volume functor
factors as
$\Phi_d = \mathrm{Sp}^{\mathrm{ch}}_{\Sigma_{d-1},C}\circ\Phi^{\mathrm{FA}}_d$,
with Stage~1 on the formal locus only (generic at $d\le 2$;
$K3\times E$ at $d=3$ via $\mathrm{At}(T_E)=0$, $\Omega^3_{K3}=0$;
compact CY$_3$ with $\mathrm{At}(TX)\neq 0$ obstructed; $d\ge 4$
open). A single CY-$d$ category admits a family of $E_1$-chiral
shadows indexed by $(\Sigma_{d-1},C)$; on $K3\times E$ the six
construction routes form a common limit cone in
$\mathrm{ChirAlg}^{E_1}_C$.

\emph{Eight-form Gritsenko--Cl\'ery spread.} Weights
$w(N)\in\{5,2,1,1,1/2,1,1/4,0\}$, Fourier zero-coefficients
$c_N(0)\in\{10,4,2,2,1,2,1/2,0\}$, universal Borcherds-weight
identity $\kappa_{\mathrm{BKM}}(\Phi_N)=c_N(0)/2$; cover assignment
$\mathrm{Sp}_4(\bZ)/\mathrm{Mp}_4(\bZ)/\widetilde{\mathrm{Mp}}_4$ by
weight parity (Weil representation plus Stone--von Neumann at
signature $(2,3)$). The additive decomposition
$\kappa_{\mathrm{BKM}}=\kappa_{\mathrm{ch}}+\chi(\cO_{\mathrm{fiber}})$
fails at every $N$, including $N=1$ ($\kappa_{\mathrm{ch}}=0$ by
Serre duality at $d=3$; $\kappa_{\mathrm{BKM}}=5$).

\emph{Three-tier topologisation.} Tier~I (cohomological) and
Tier~II (chain level on a quasi-isomorphic model, via Fresse
Theorem~12.3.A homotopy transfer) are unconditional. Tier~III
(strict chain level on the original complex) is closed for
$\mathsf G$, $\mathsf L$, $\mathsf C$ and open for $\mathsf M$ (F3).
Sugawara explicit at $V_1(\mathfrak{sl}_2)$:
$T_{\mathrm{Sug}}=(1/6)(\mathord{:}J^0J^0\mathord{:}
+\mathord{:}J^+J^-\mathord{:}+\mathord{:}J^-J^+\mathord{:})$,
$G_{\mathrm{Sug}}=(1/3)\sum_a\mathord{:}\bar c_a J^a\mathord{:}$,
$[Q_{\mathrm{tot}},G_{\mathrm{Sug}}]=T_{\mathrm{Sug}}$ on BRST
cohomology.

\emph{Shadow tower closed forms.} Borel radius
$|\omega|^2(c)=c^2(5c+22)/[4(45c+218)]$, Stokes pole $c_S=-218/45$;
shadow coefficient
$S_6(\mathrm{Vir}_c)=4(240c+1031)/[c^3(5c+22)^2]$; Riccati on
$U=(\log H)'-2/t$ satisfying $U'+2U^2=Q_c''/(2Q_c)$.

\emph{Ten named frontiers.} Logarithmic $\cW(p)$ tempering (F1);
periodic CDG for non-simply-laced admissible levels (F2);
original-complex Tier~III for class $\mathsf M$ (F3);
super-complementarity canonical pairing (F4); irregular-singular KZB
at $\overline{\cM}_{g,n}$ boundaries with Drinfeld-double
obstruction $\mathrm{obs}^{(1)}_{\mathrm{double}}\in
H^2(\mathfrak{grt}^{\mathrm{ell}},\mathfrak{sp}(\cA)\otimes\mathfrak{sp}(\cA^!))$
vanishing iff $r_{\max}(\cA)=2$ (F5); Theorem~B at nodal boundary
without Koszul hypothesis (F6); MC4 completion / H3 failure regime
(F7); Stage-1 chain level at $d\ge 4$ (F8); category-level
$E_d$-formality at $d\ge 4$ (F9); bracket-level BPS Lie algebra on
$K3\times E$ (F10).

% =====================================================================
% End of Programme Overview.
% =====================================================================
