\chapter[Combinatorial frontier]{The combinatorial frontier of chiral bar cohomology}
\label{app:combinatorial-frontier}

Combinatorics in this monograph is not incidental decoration on an
algebraic core; it is constitutive.  The dimensions
$\dim H^n(\barBgeom(\cA))$ are integers, and integers have structure:
generating functions, recurrences, growth rates, OEIS identities.
The bar-cobar machine converts algebraic input (OPE data, relation
spaces, conformal weights) into integer sequences, and those sequences
carry information about the algebra that no single theorem statement
can capture.  When $\dim(\mathrm{Vir}^!)_n$ grows as $3^n/n^{3/2}$
while $\dim(\beta\gamma^!)_n$ grows as $3^n/n^{1/2}$, the shared
base and differing exponent encode the fact that these algebras share
a spectral discriminant but differ in the multiplicity structure of
their Koszul duals.

The counting problem has a further layer: one wants to count not only
bar cohomology dimensions but coherent packages (shadow-compatible
families of invariants), primitive modular characteristics (the
irreducible pieces of the completed Maurer--Cartan element), and
stratified contributions from each boundary stratum of
$\overline{\mathcal{M}}_{g,n}$.  The tables below organize
the known data and mark the boundary between computed, conjectured
from generating functions, and genuinely unknown.

This chapter consolidates all known enumerative data arising from the chiral bar-cobar theory and organizes the computational frontier.  The sequences, generating functions, and numerical invariants below are the \emph{shadow-level} (S-level) output of the algebraic machinery developed in Parts~1--3; each entry records the theorem or conjecture from which it derives, its current verification status, and the obstruction to further computation.

\medskip
\noindent\emph{Principle.}
For a Koszul chiral algebra~$\cA$, the bar cohomology dimensions $\dim H^n(\barBgeom(\cA))$ coincide with the Hilbert function of the Koszul dual $\cA^!$ (Corollary~\ref{cor:bar-cohomology-koszul-dual}).  These dimensions are the central enumerative invariants of the theory.  Their generating functions encode, in compact form, the full structure of the bar complex: growth rates, analytic singularities, and (conjecturally) the spectral data of a finite-rank transfer operator.

\section{Master table of bar cohomology dimensions}
\label{sec:master-table-frontier}

Table~\ref{tab:frontier-bar-dims} extends Table~\ref{tab:bar-dimensions} with additional algebras and deeper commentary on the status of each entry.

\begin{table}[ht]
\centering
\caption{Bar cohomology dimensions $\dim(\cA^!)_n$ through degree~$10$.
$\bullet$\,=\,proved, $\circ$\,=\,conjectured from GF/recurrence, blank\,=\,unknown.}
\label{tab:frontier-bar-dims}
\resizebox{\textwidth}{!}{%
\renewcommand{\arraystretch}{1.35}%
\begin{tabular}{|l|ccccccccccc|l|l|}
\hline
\textbf{Algebra $\cA$}
  & \textbf{0} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{9} & \textbf{10}
  & \textbf{Growth} & \textbf{OEIS} \\
\hline
Heisenberg ($\mathrm{rk}\,1$)
  & $\bullet 1$ & $\bullet 1$ & $\bullet 1$ & $\bullet 1$ & $\bullet 2$ & $\bullet 3$ & $\bullet 5$ & $\bullet 7$ & $\bullet 11$ & $\bullet 15$ & $\bullet 22$
  & $e^{c\sqrt{n}}$ & A000041 \\
\hline
Free fermion $\psi$
  & $\bullet 1$ & $\bullet 1$ & $\bullet 1$ & $\bullet 2$ & $\bullet 3$ & $\bullet 5$ & $\bullet 7$ & $\bullet 11$ & $\bullet 15$ & $\bullet 22$ & $\bullet 30$
  & $e^{c\sqrt{n}}$ & A000041 \\
\hline
$bc$ ghosts
  & $\bullet 1$ & $\bullet 2$ & $\bullet 3$ & $\bullet 6$ & $\bullet 13$ & $\bullet 28$ & $\bullet 59$ & $\bullet 122$ & $\bullet 249$ & $\bullet 504$ & $\bullet 1013$
  & $2^n$ & A132045 \\
\hline
$\beta\gamma$ system
  & $\bullet 1$ & $\bullet 2$ & $\bullet 4$ & $\bullet 10$ & $\bullet 26$ & $\bullet 70$ & $\bullet 192$ & $\bullet 534$ & $\bullet 1500$ & $\bullet 4246$ & $\bullet 12092$
  & $3^n / n^{1/2}$ & A025565 \\
\hline
$\widehat{\mathfrak{sl}}_2$
  & $\bullet 1$ & $\bullet 3$ & $\bullet 5$ & $\bullet 15$ & $\bullet 36$ & $\bullet 91$ & $\bullet 232$ & $\bullet 603$ & $\bullet 1585$ & $\bullet 4213$ & $\bullet 11298$
  & $3^n / n^{3/2}$ & --- \\
\hline
$\widehat{\mathfrak{sl}}_3$
  & $\bullet 1$ & $\bullet 8$ & $\bullet 36$ & $\bullet 204$ & $\circ 1352$ & $\circ 9892$ & $\circ 76084$ & $\circ 598592$ & $\circ 4755444$ & $\circ 37963948$ & $\circ 303961012$
  & $8^n$ & --- \\
\hline
$\mathrm{Vir}_c$
  & $\bullet 1$ & $\bullet 1$ & $\bullet 2$ & $\bullet 5$ & $\bullet 12$ & $\bullet 30$ & $\bullet 76$ & $\bullet 196$ & $\bullet 512$ & $\bullet 1353$ & $\bullet 3610$
  & $3^n / n^{3/2}$ & A002026 \\
\hline
$\mathcal{W}_3$
  & $\bullet 1$ & $\bullet 2$ & $\bullet 5$ & $\bullet 16$ & $\bullet 52$ & $\circ 171$ & $\circ 564$ & $\circ 1862$ & $\circ 6149$ & $\circ 20305$ & $\circ 67044$
  & $3.30^n$ & --- \\
\hline
$Y(\mathfrak{sl}_2)$
  & $\bullet 1$ & $\bullet 4$ & $\bullet 10$ & $\bullet 28$ & $\circ 82$ & $\circ 244$ & $\circ 730$ & $\circ 2188$ & $\circ 6562$ & $\circ 19684$ & $\circ 59050$
  & $3^n$ & --- \\
\hline
$\widehat{G}_{2,k}$
  & $\bullet 1$ & $\bullet 14$ & & & & & & & & &
  & $14^n$ (pred.) & --- \\
\hline
$\widehat{\mathfrak{sp}}_{4,k}$
  & $\bullet 1$ & $\bullet 10$ & & & & & & & & &
  & $10^n$ (pred.) & --- \\
\hline
\end{tabular}
}

\medskip
\noindent
{\footnotesize
$\bullet$\,Proved values derive from:
PBW spectral sequence collapse (Theorem~\ref{thm:spectral-sequence-collapse}),
chiral Koszulness (Theorems~\ref{thm:km-chiral-koszul},
\ref{thm:virasoro-chiral-koszul}),
and explicit computation of the bar differential rank.
$\circ$\,Conjectured values derive from fitting a rational or algebraic
generating function to the proved data points; see
Conjectures~\ref{conj:sl3-bar-gf}, \ref{conj:w3-algebraicity},
\ref{conj:yangian-bar-gf}.
For $\widehat{G}_{2,k}$ and $\widehat{\mathfrak{sp}}_{4,k}$,
only $H^0 = 1$ and $H^1 = \dim\mathfrak{g}$ are known
(the latter by Whitehead).
}
\end{table}

\begin{remark}[Reading the table]
\label{rem:reading-frontier-table}
The zeroth column ($n=0$) is always~$1$: the augmentation $\cA \to \mathbb{C}$ contributes a one-dimensional class in bar degree zero.  The first column ($n=1$) equals $\dim\overline{\cA}_{[1]}$, the dimension of the weight-$1$ augmentation ideal.  For Kac--Moody algebras $\widehat{\mathfrak{g}}_k$, this is $\dim\mathfrak{g}$; for the Virasoro algebra, it is~$1$ (the single generator~$T$); for $\mathcal{W}_3$, it is~$2$ (generators $T$ and~$W$).

\emph{The data is level-independent.}  For every algebra in the table, the bar cohomology dimensions are independent of the level~$k$ (or central charge~$c$) at generic values.  This is a deep consequence of the PBW spectral sequence structure: the $E_1$ page is a Lie algebra cohomology computation that depends only on the underlying finite-dimensional data $(\mathfrak{g}, \dim\mathfrak{g}, h^\vee)$, not on the level (this follows from the PBW spectral sequence: at generic level the $E_2$ page is level-independent, and concentration at $E_2$ gives the result; see Theorem~\ref{thm:master-pbw}).  The level enters only through the curvature term $\omega_g$ at genus $g \geq 1$, which affects the genus expansion (Theorem~\ref{thm:genus-universality}) but not the bar cohomology dimensions themselves.
\end{remark}

\section{Named combinatorial sequences}
\label{sec:named-sequences}

Six classical combinatorial sequences appear as bar cohomology dimensions.  For each, we record the sequence definition, the mechanism by which it arises, and the OEIS reference.

\subsection{Partition numbers (Heisenberg, free fermion)}
\label{subsec:partition-numbers}

The partition function $p(n) = |\{\lambda \vdash n\}|$ (OEIS~A000041) enumerates integer partitions.

\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|cccccccccc}
$n$ & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
\hline
$p(n)$ & 1 & 1 & 2 & 3 & 5 & 7 & 11 & 15 & 22 & 30
\end{tabular}
\end{center}

\emph{How it appears.}
The Heisenberg algebra $\mathcal{H}_k$ has $\dim(\mathcal{H}_k^!)_n = p(n-2)$ for $n \geq 2$ and $\dim(\mathcal{H}_k^!)_0 = \dim(\mathcal{H}_k^!)_1 = 1$ (Theorem~\ref{thm:heisenberg-bar}).  The free fermion $\psi$ has $\dim(\psi^!)_n = p(n-1)$.  Both identifications follow from the structure of the augmentation ideal: the Heisenberg is generated by a single bosonic field $\alpha(z)$ of weight~$1$, whose descendants $\alpha_{-n}$ ($n \geq 1$) form an abelian Lie algebra isomorphic to $\mathbb{C}[t^{-1}]t^{-1}$.  The bar complex reduces to the exterior algebra of this abelian Lie algebra, graded by conformal weight, and the weight-$h$ component has dimension~$p(h)$.

\emph{Generating function.}
The partition function has the celebrated Euler product:
\[
\sum_{n \geq 0} p(n)\, q^n = \prod_{k=1}^{\infty} \frac{1}{1 - q^k}
= \frac{1}{\eta(q) \cdot q^{-1/24}},
\]
where $\eta(q) = q^{1/24}\prod_{n \geq 1}(1-q^n)$ is the Dedekind eta function.  This is the genus-$1$ partition function of the free boson (Theorem~\ref{thm:genus1-heisenberg}).  The transcendence of this generating function (it is not algebraic over $\mathbb{Q}(q)$) reflects the abelian, non-interacting nature of the Heisenberg algebra.

\emph{Asymptotics.}
Hardy--Ramanujan: $p(n) \sim e^{\pi\sqrt{2n/3}}/(4\sqrt{3}\,n)$, sub-exponential growth.  This characterizes free fields among Koszul chiral algebras (Corollary~\ref{cor:subexp-free-field}).

\begin{remark}[Partition numbers in MC3 thick generation]%
\label{rem:partition-mc3-bridge}%
\index{partition function!MC3 bridge}%
\index{thick generation!partition function bridge}%
The partition function~$p(k)$ appears in a second, independent role
as the weight multiplicity of the Yangian negative prefundamental
module: $\dim(L^-_a)_{-2k} = p(k)$.  This creates a direct bridge
between the combinatorial data of the bar complex (Frame~A) and the
MC3 thick generation programme (Frame~B):
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item The kernel $K := \operatorname{ch}(L^-) - \operatorname{ch}(M(0))$
  has coefficient $p(m) - 1$ at weight~$-2m$, which equals the
  cumulative partition function $\sum_{k \leq m} p_2(k)$
  (partitions into parts~$\geq 2$).
\item Subtracting $\operatorname{ch}(L^-(\mathrm{hw} = -4))$ from~$K$
  yields a residual with coefficient $p(m) - 1 - p(m-2)$,
  recovering~$p(k)$ by a self-similar recursion
  (Remark~\ref{rem:eval-stability-recursive-kernel}).
\item The Euler characteristic
  $\chi(L^-, V_n) = \sum_{k=0}^{n/2} p(k)$ for even~$n$
  recovers partial sums of the partition function from the
  Hom/Ext structure of the Yangian category.
\end{enumerate}
This bridge is verified by $80$+~tests across
\texttt{test\_prefundamental\_clebsch\_gordan},
\texttt{test\_prefundamental\_cg\_closure},
and \texttt{test\_thick\_generation\_sl2}.
\end{remark}

\subsection{Riordan numbers ($\widehat{\mathfrak{sl}}_2$)}
\label{subsec:riordan}

The Riordan numbers $R(n)$ (OEIS~A005043) satisfy the recurrence
\begin{equation}\label{eq:riordan-recurrence}
(n+1)\,R(n) = (n-1)\bigl(2R(n-1) + 3R(n-2)\bigr),
\qquad R(0) = 1,\; R(1) = 0,
\end{equation}
with generating function
\begin{equation}\label{eq:riordan-gf}
\sum_{n \geq 0} R(n)\,x^n
= \frac{1 + x - \sqrt{1-2x-3x^2}}{2x(1+x)}\,.
\end{equation}

\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|cccccccccccc}
$n$ & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\
\hline
$R(n)$ & 1 & 0 & 1 & 1 & 3 & 6 & 15 & 36 & 91 & 232 & 603 & 1585
\end{tabular}
\end{center}

\emph{How it appears.}
The Riordan numbers were originally predicted to give
$\dim(\widehat{\mathfrak{sl}}_{2,k}^!)_n = R(n+3)$ for all
$n \geq 0$, based on the $E_1$ page of the PBW spectral
sequence (Theorem~\ref{thm:universal-kac-moody-koszul}).
However, the $E_2$ collapse
(Corollary~\ref{cor:bar-cohomology-koszul-dual},
Remark~\ref{rem:ce-vs-exterior}) shows that the bar
cohomology is computed by the Chevalley--Eilenberg
cohomology of $\mathfrak{sl}_2 \otimes t^{-1}\bC[t^{-1}]$,
which gives $\dim H^1 = 3 = R(4)$ (agreement) but
$\dim H^2 = 5 \neq 6 = R(5)$ (discrepancy at degree~$2$).
The $E_1$ dimensions
$\prod_{m \geq 1}(1+q^m)^3 = 1, 3, 6, 13, 24, \ldots$
(by conformal weight) agree with $R(h+3)$ at
$h = 0, 1, 2$ but diverge at $h \geq 3$
($13 \neq R(6) = 15$).
The correct bar cohomology dimensions are the CE values
$\dim H^n = 3, 5, \ldots$ for $n = 1, 2, \ldots$;
the Riordan identification requires revision.

\emph{Combinatorial interpretation.}
Riordan numbers count several classical objects~\cite{BernhartRiordan}: Motzkin paths of length~$n$ that never touch the $x$-axis except at endpoints; non-crossing partitions of $\{1, \ldots, n\}$ without singleton blocks; and certain classes of restricted lattice paths.  Their brief appearance in the old chiral bar-cohomology count motivates the \emph{conjectural} search for a combinatorial model of the $\widehat{\mathfrak{sl}}_2$ bar complex in terms of non-crossing structures, analogous to the Motzkin-path model for the Virasoro algebra (Theorem~\ref{thm:motzkin-path-model}).  No such model has been constructed.

\emph{Asymptotics.}
$R(n) \sim (3/4)\sqrt{3/\pi}\, n^{-3/2}\, 3^n$ (from the square-root singularity at $x = 1/3$).  The growth rate~$3^n = (\dim\mathfrak{sl}_2)^n$ is sharp: the chain-space bound $\dim\bar{B}^n \leq (\dim\mathfrak{g})^n \cdot (n-1)!$ shows that the exponential growth rate of bar cohomology cannot exceed $\dim\mathfrak{g}$ (Corollary~\ref{cor:growth-rate-dimg}), and for $\widehat{\mathfrak{sl}}_2$ this bound is saturated.

\subsection{Motzkin numbers and their differences (Virasoro)}
\label{subsec:motzkin}

The Motzkin numbers $M(n)$ (OEIS~A001006) count lattice paths from $(0,0)$ to $(n,0)$ using up steps $(1,1)$, down steps $(1,-1)$, and flat steps $(1,0)$, staying at height $\geq 0$.

\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|cccccccccccc}
$n$ & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\
\hline
$M(n)$ & 1 & 1 & 2 & 4 & 9 & 21 & 51 & 127 & 323 & 835 & 2188 & 5798 \\
$M(n{+}1) - M(n)$ & 0 & 1 & 2 & 5 & 12 & 30 & 76 & 196 & 512 & 1353 & 3610 & 9694
\end{tabular}
\end{center}

\emph{How it appears.}
$\dim(\mathrm{Vir}_c^!)_n = M(n+1) - M(n)$ for all $n \geq 1$ (Theorem~\ref{thm:spectral-sequence-collapse}).  The differences $M(n+1) - M(n)$ (OEIS~A002026) count $U$-initial Motzkin paths of length~$n+1$, i.e., Motzkin paths whose first step is an up step.  This count has a direct representation-theoretic meaning: the bijection of Theorem~\ref{thm:motzkin-path-model} associates to each basis element of $H^n(\barBgeom(\mathrm{Vir}_c))$ a $U$-initial Motzkin path, with the three step types corresponding to the three singular terms in the Virasoro OPE $T(z)T(w)$.

\emph{Generating function.}
\[
\sum_{n \geq 0} M(n)\,x^n
= \frac{1 - x - \sqrt{1-2x-3x^2}}{2x^2}\,,
\]
sharing the discriminant $\Delta(x) = 1-2x-3x^2 = (1-3x)(1+x)$ with the Riordan generating function.  This shared discriminant is the signature of the $\mathfrak{sl}_2$ DS family (Theorem~\ref{thm:ds-bar-gf-discriminant}).

\emph{The Motzkin recurrence.}
$(n+2)\,M(n) = (2n+1)\,M(n-1) + 3(n-1)\,M(n-2)$, equivalent to the algebraic equation $x^2 M^2 + (x-1)M + 1 = 0$.  The $P$-recursive structure reflects the Koszul property: bar cohomology dimensions of Koszul chiral algebras satisfy holonomic recurrences.

\subsection{Partition functions and the prefundamental bridge (MC3)}
\label{subsec:partition-prefundamental}
\index{partition function!prefundamental bridge}
\index{thick generation!partition function}

The integer partition function~$p(k)$ (OEIS~A000041)
appears in two apparently independent roles:

\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item \emph{Free-field bar complex dimensions}:
  $\dim\bar{B}^n(\psi) = p(n-1)$ for the free fermion
  (Lemma~\ref{lem:bar-dims-partitions}).
\item \emph{Yangian prefundamental weight multiplicities}:
  $\dim(L^-_a)_{-2k} = p(k)$ for the negative prefundamental module
  of~$Y(\mathfrak{sl}_2)$
  (Theorem~\ref{thm:shifted-prefundamental-generation}, Step~2).
\end{enumerate}

\noindent
The coincidence is not accidental: both arise from the
Euler product $\prod_{n \geq 1}(1-q^n)^{-1}$, which is
the character of the bosonic Fock space (the universal
enveloping algebra of the Heisenberg Lie algebra in the
negative-mode sector).

\emph{The prefundamental Clebsch--Gordan (R1).}
The decomposition $V_n \otimes L^- \cong \bigoplus_{j=0}^{n}
L^-(n-2j)$ at character level (verified $n = 1, \ldots, 8$,
depth~$40$) implies that the tensor product ring of the
Yangian category~$\mathcal{O}$ is governed by partition-function
arithmetic: the multiplicities in $V_n \otimes L^-$ at weight~$w$
are convolutions of partition numbers.

\emph{The kernel decomposition (R2).}
The kernel $K := \operatorname{ch}(L^-) - \operatorname{ch}(M(0))$
has $K_{-2m} = p(m) - 1$ for all~$m \geq 0$
(verified to depth~$100$).
This is the sequence of partitions with~$\geq 2$ parts (OEIS~A000065),
connecting the MC3 thick generation obstruction to classical
partition combinatorics.

\emph{Growth rate.}
$\log\delta(k) = \log(p(k)-1) \sim \pi\sqrt{2k/3}$
(Hardy--Ramanujan), which is sub-exponential.  This matches the
$E_1$-page growth from
Proposition~\ref{prop:lqt-e1-subexponential-growth}:
the resolution complexity of expressing Verma modules from
prefundamentals is compatible with the bar-cobar formalism.

\subsection{Catalan numbers (A-infinity, associahedra)}
\label{subsec:catalan}

The Catalan numbers $C_n = \frac{1}{n+1}\binom{2n}{n}$ (OEIS~A000108) appear not as bar cohomology dimensions directly, but as the combinatorial skeleton underlying the homotopy transfer machinery.

\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|cccccccccc}
$n$ & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
\hline
$C_n$ & 1 & 1 & 2 & 5 & 14 & 42 & 132 & 429 & 1430 & 4862
\end{tabular}
\end{center}

\emph{How they appear.}

\begin{enumerate}[label=(\roman*)]
\item \emph{Planar rooted trees.}  The number of planar rooted trees with~$n$ internal nodes is $C_{n-1}$.  These trees index the terms of the $A_\infty$ structure maps $m_n$ in the homotopy transfer theorem (Appendix~\ref{app:homotopy-transfer}, Theorem~\ref{thm:htt}).  When one transfers the bar complex structure to a minimal model via a strong deformation retract, each $m_n$ is a sum over $C_{n-1}$ planar trees.

\item \emph{Associahedra.}  The associahedron $K_n$ has $C_{n-1}$ vertices (maximal bracketings of an $(n+1)$-fold product).  The FM compactification $\overline{C}_n(\mathbb{P}^1) \cong K_n$ of the genus-$0$ configuration space is isomorphic to the associahedron as a stratified space (Theorem~\ref{thm:fm-associahedron}).  The Betti numbers of $K_n$ are related to Narayana numbers, and the $f$-vector encodes the bar spectral sequence page dimensions.

\item \emph{Virasoro at low degree.}  The first few Virasoro bar cohomology dimensions $(1, 2, 5, 12, 30)$ begin with a Catalan-adjacent pattern: $C_1 = 1$, $C_2 = 2$, $C_3 = 5$.  The agreement is not coincidental but breaks at $n = 4$ ($C_4 = 14 \neq 12$), reflecting the distinction between the full Catalan enumeration and the Motzkin-difference count.
\end{enumerate}

\subsection{Bernoulli numbers (genus expansion)}
\label{subsec:bernoulli}

The Bernoulli numbers $B_{2g}$ (OEIS~A027642 for denominators) govern the genus expansion of every Koszul chiral algebra.

\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|cccccccccc}
$g$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
\hline
$|B_{2g}|$ & $\tfrac{1}{6}$ & $\tfrac{1}{30}$ & $\tfrac{1}{42}$ & $\tfrac{1}{30}$ & $\tfrac{5}{66}$ & $\tfrac{691}{2730}$ & $\tfrac{7}{6}$ & $\tfrac{3617}{510}$ & $\tfrac{43867}{798}$ & $\tfrac{174611}{330}$
\end{tabular}
\end{center}

\emph{How they appear.}
The Faber--Pandharipande coefficients
\[
\lambda_g^{FP} = \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}
\]
are the universal genus-$g$ obstruction coefficients (Proposition~\ref{prop:fp-coefficients}).  For any Koszul chiral algebra~$\cA$, the genus-$g$ free energy factors as $F_g(\cA) = \kappa(\cA) \cdot \lambda_g^{FP}$ (Theorem~\ref{thm:genus-universality}).  The generating function
\[
\sum_{g \geq 1} \lambda_g^{FP}\, x^{2g}
= \frac{x/2}{\sin(x/2)} - 1
= \hat{A}(x) - 1,
\]
where $\hat{A}(x) = x/2 / \sinh(x/2)$ is the $\hat{A}$-genus, is the even part of the Todd class.  The appearance of Bernoulli numbers via the $\hat{A}$-genus is a manifestation of the index-theoretic nature of genus corrections: the bar complex curvature at genus~$g$ is controlled by the Hodge bundle on $\overline{\mathcal{M}}_g$, and the Faber--Pandharipande formula is an intersection-theoretic avatar of the Hirzebruch--Riemann--Roch theorem.

\emph{Asymptotics.}
$\lambda_g^{FP} \sim 2/(2\pi)^{2g}$, super-exponential decay.  This guarantees convergence of the genus expansion $\sum_g F_g(\cA)\,x^{2g}$ for all finite~$\kappa$ (Proposition~\ref{prop:bivariate-gf}).

\subsection{Stirling numbers (configuration spaces)}
\label{subsec:stirling}

The unsigned Stirling numbers of the first kind $|s(n,k)| = e_k(1, 2, \ldots, n-1)$ (elementary symmetric polynomials evaluated at $1, \ldots, n-1$) appear as Betti numbers of configuration spaces.

\emph{How they appear.}
The Poincar\'e polynomial of the configuration space $C_n(\mathbb{C})$ is
\[
P_t(C_n(\mathbb{C})) = \prod_{j=1}^{n-1}(1+jt)
= \sum_{k=0}^{n-1} e_k(1, 2, \ldots, n-1)\, t^k,
\]
so $\dim H^k(C_n(\mathbb{C})) = e_k(1, \ldots, n-1)$.  In particular:
\begin{itemize}
\item $\dim H^0 = 1$ (connected);
\item $\dim H^1 = \binom{n}{2}$ (Arnold generators $\eta_{ij}$);
\item $\dim H^{n-1} = (n-1)!$ (top degree; equals $\dim\mathrm{OS}^{n-1}(n)$).
\end{itemize}
The top-degree dimension $(n-1)!$ directly enters the chain-group formula: $\dim\bar{B}^n(\widehat{\mathfrak{g}}_k) = (\dim\mathfrak{g})^n \cdot (n-1)!$ (Lemma~\ref{lem:bar-dims-level-independent}).  The factorial growth of the chain space, contrasted with the exponential growth of bar cohomology, measures the efficiency of the bar differential: cancellation accounts for $(n-1)!/(\dim\mathfrak{g})^n$ of the chain space at leading order.


\section{Generating functions: the algebraic hierarchy}
\label{sec:gf-hierarchy}

The generating functions of bar cohomology dimensions fall into a strict hierarchy of algebraic complexity.  This hierarchy reflects the interaction structure of the underlying chiral algebra.

\subsection{Transcendental (free fields)}
\label{subsec:gf-transcendental}

\begin{align}
P_{\mathcal{H}}(q) &= \prod_{k \geq 1} \frac{1}{1-q^k}
&&\text{(Heisenberg; weight-graded)} \\
P_{\psi}(q) &= \prod_{k \geq 1} (1+q^k)
&&\text{(free fermion; weight-graded)}
\end{align}

These are modular objects (related to $1/\eta(\tau)$ and $\eta(2\tau)/\eta(\tau)$ respectively).  Their transcendence over $\mathbb{Q}(q)$ is a consequence of the Nesterenko--Bertrand theorem on modular transcendence.  No polynomial differential equation over $\mathbb{Q}(q)$ is satisfied.  This reflects the absence of nontrivial OPE poles: the bar differential is zero, and the bar cohomology is the full chain space.

\emph{Conformal-weight-collapsed series.}  If one forgets the conformal weight grading and counts only by bar degree, the Heisenberg dimensions become $\dim(\mathcal{H}^!)_n \in \{1, 1, 1, 2, 3, 5, 7, 11, \ldots\} = p(n-2)$ (Table~\ref{tab:frontier-bar-dims}).

\subsection{Rational (bc ghosts, Yangian)}
\label{subsec:gf-rational}

\begin{align}
P_{bc}(x) &= \sum_{n \geq 1}(2^n - n + 1)\,x^n
&&\text{(closed form: $\frac{2x}{1-2x} - \frac{x}{(1-x)^2} + \frac{x}{1-x}$)}
\label{eq:bc-gf}
\end{align}

The $bc$ ghost system has a rational generating function because its OPE is purely fermionic with a single pole of order~$1$: the bar differential is maximally sparse, and the cohomology computation reduces to a subtraction of two geometric series.

\emph{Yangian (conjectured).}
$P_{Y(\mathfrak{sl}_2)}(x) = (1-3x^2)/((1-x)(1-3x))$ (Conjecture~\ref{conj:yangian-bar-gf}).  If confirmed, this would be the only \emph{interacting} algebra with a rational bar generating function.  The partial fraction decomposition $-1 + 1/(1-x) + 1/(1-3x)$ suggests a K\"unneth-type splitting into a ``$\mathfrak{gl}_1$ center'' contribution ($1/(1-x)$, polynomial growth) and an ``$\mathfrak{sl}_2$ factor'' contribution ($1/(1-3x)$, exponential growth $3^n$).  This splitting is consistent with the RTT presentation of $Y(\mathfrak{sl}_2)$ (Theorem~\ref{thm:yangian-bar-rtt}).

\emph{Why rationality is surprising.}
For $E_\infty$-chiral algebras (Kac--Moody, Virasoro), the bar generating function is algebraic of degree~$2$ over $\mathbb{Q}(x)$ (Corollary~\ref{cor:algebraicity-koszul}).  The Yangian is $E_1$-chiral, not $E_\infty$, and the rationality of its bar GF may reflect the stronger algebraic constraints of the $E_1$ structure (full associativity of the chiral product, not just homotopy associativity).

\subsection{Algebraic of degree 2 ($\mathfrak{sl}_2$ family)}
\label{subsec:gf-algebraic}

The three algebras in the $\mathfrak{sl}_2$ DS orbit share a common discriminant:

\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lll}
\toprule
\textbf{Algebra} & \textbf{Generating function} & \textbf{Singularity type} \\
\midrule
$\widehat{\mathfrak{sl}}_2$ & $(1+x-\sqrt{\Delta})\,/\,(2x(1+x))$ & $\Delta^{1/2}$ \\
$\mathrm{Vir}_c$ & $4x\,/\,(1-x+\sqrt{\Delta})^2$ & $\Delta^{1/2}$ \\
$\beta\gamma$ & $(1+x)\,/\,\sqrt{\Delta}$ & $\Delta^{-1/2}$ \\
\bottomrule
\end{tabular}
\end{center}
where $\Delta(x) = (1-3x)(1+x) = 1-2x-3x^2$.

\emph{Why the same discriminant.}
Drinfeld--Sokolov reduction $\widehat{\mathfrak{sl}}_2 \twoheadrightarrow \mathrm{Vir}_c$ preserves the discriminant (Theorem~\ref{thm:ds-bar-gf-discriminant}).  The Wakimoto representation $\widehat{\mathfrak{sl}}_2 \hookrightarrow \beta\gamma \otimes \mathcal{H}$ transmits the discriminant to the $\beta\gamma$ factor (the Heisenberg tensor factor contributes only sub-exponential corrections).  The invariance of the discriminant under DS reduction is the first proved instance of a general principle (Proposition~\ref{prop:discriminant-characteristic}).

\emph{The branch points.}
$x = 1/3$: the dominant singularity, giving exponential growth $3^n = (\dim\mathfrak{sl}_2)^n$.  $x = -1$: the subdominant singularity, giving alternating corrections $(-1)^n$.  The two eigenvalues of the Picard--Fuchs companion matrix $T_{\mathrm{rec}} = \bigl(\begin{smallmatrix} 2 & 3 \\ 1 & 0 \end{smallmatrix}\bigr)$ are precisely $3$ and $-1$ (Proposition~\ref{prop:hred-sl2}).

\subsection{Conjectured rational ($\mathfrak{sl}_3$ family)}
\label{subsec:gf-sl3-family}

The $\mathfrak{sl}_3$ DS orbit is conjectured to have \emph{rational} (not algebraic) generating functions sharing the denominator factor $(1-3x-x^2)$:

\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lll}
\toprule
\textbf{Algebra} & \textbf{Conjectured GF} & \textbf{Denominator} \\
\midrule
$\widehat{\mathfrak{sl}}_3$ & $4x(2-13x-2x^2)\,/\,\bigl((1-8x)(1-3x-x^2)\bigr)$ & $(1-8x)(1-3x-x^2)$ \\
$\mathcal{W}_3$ & $x(2-3x)\,/\,\bigl((1-x)(1-3x-x^2)\bigr)$ & $(1-x)(1-3x-x^2)$ \\
\bottomrule
\end{tabular}
\end{center}

\begin{conjecture}[\texorpdfstring{$\mathcal{W}_3$}{W3} bar cohomology generating function; \ClaimStatusConjectured]\label{conj:w3-bar-gf}
The bar cohomology generating function of the $\mathcal{W}_3$ algebra is
\[
P_{\mathcal{W}_3}(x) = \frac{x(2-3x)}{(1-x)(1-3x-x^2)},
\]
with denominator polynomial $D(x) = 1 - 4x + 2x^2 + x^3 = (1-x)(1-3x-x^2)$.  This predicts the linear recurrence $a_k = 4a_{k-1} - 2a_{k-2} - a_{k-3}$ for $k \geq 4$, with initial values $a_1 = 2$, $a_2 = 5$, $a_3 = 16$, $a_4 = 52$.
\end{conjecture}

\begin{construction}[Combinatorial frontier as class~$\mathsf{M}$ shadow data]
\label{constr:combinatorial-frontier-shadow}
The quasi-polynomial structure of $\mathcal{W}_3$ bar cohomology
dimensions is a consequence of the infinite shadow tower
(class~$\mathsf{M}$, $r_{\max} = \infty$): the $L_\infty$
obstruction $o_{r+1}(\mathcal{W}_3)$ is nonzero for all
$r \geq 3$, generating quasi-polynomial growth with period
determined by the denominator of the quartic contact invariant
$Q^{\mathrm{contact}}_{\mathrm{Vir}} = 10/[c(5c+22)]$.
The mechanism is as follows.
\begin{enumerate}[label=\textup{(\roman*)}]
\item The shadow Postnikov tower
  $\Theta_{\mathcal{W}_3}^{\leq r}$
  (Definition~\ref{def:shadow-postnikov-tower}) is the
  projection of the bar-intrinsic MC element
  $\Theta_{\mathcal{W}_3} := D_{\mathcal{W}_3} - d_0$
  (Theorem~\ref{thm:mc2-bar-intrinsic}) to arity~$\leq r$.
  For class~$\mathsf{M}$ algebras, each successive
  obstruction class $o_{r+1}(\mathcal{W}_3)
  \in H^2(F^{r+1}\mathfrak{g}/F^{r+2}\mathfrak{g}, d_2)$
  is nonzero, so the tower does not terminate.
\item The linear recurrence
  $a_k = 4a_{k-1} - 2a_{k-2} - a_{k-3}$
  (Conjecture~\ref{conj:w3-bar-gf}) is the
  shadow-level reflection of this nontermination: the
  characteristic polynomial
  $(1-x)(1-3x-x^2)$ of the recurrence encodes the
  DS-invariant discriminant, while the degree-$3$
  denominator (one unit higher than the rank of
  $\mathfrak{sl}_3$) records the persistent
  nonvanishing of the quartic and higher obstruction
  classes.
\item The contrast with class~$\mathsf{G}$ (Heisenberg,
  $r_{\max} = 2$, sub-exponential growth) and
  class~$\mathsf{L}$ ($\widehat{\mathfrak{sl}}_2$,
  $r_{\max} = 3$, algebraic GF) illustrates the
  shadow-depth classification: the combinatorial complexity
  of the bar cohomology sequence is controlled by the
  $L_\infty$-formality level of the algebra
  (Conjecture~\ref{conj:operadic-complexity}).
\end{enumerate}
\end{construction}

\emph{Characteristic polynomial.}
The recurrence $a(n) = 11a(n{-}1) - 23a(n{-}2) - 8a(n{-}3)$ for $\widehat{\mathfrak{sl}}_3$ has characteristic polynomial $t^3 - 11t^2 + 23t + 8 = (t-8)(t^2-3t-1)$.  The factorization mirrors the $\mathfrak{sl}_2$ case: the dominant root $t = 8 = \dim\mathfrak{sl}_3$ corresponds to the growth pole, while the quadratic factor $t^2 - 3t - 1$ is the reciprocal polynomial of the DS-invariant discriminant $1 - 3x - x^2$.  Its roots are $(3 \pm \sqrt{13})/2$.

\section{Discriminant families and DS orbits}
\label{sec:discriminant-families}

The discriminant of the bar generating function is a Drinfeld--Sokolov invariant (Theorem~\ref{thm:ds-bar-gf-discriminant}).  This organizes the computed examples into families.

\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{llll}
\toprule
\textbf{Family} & \textbf{DS-invariant factor} & \textbf{Roots} & \textbf{Members} \\
\midrule
$\mathfrak{sl}_2$ & $(1-3x)(1+x)$ & $1/3,\; -1$ & $\widehat{\mathfrak{sl}}_2$, $\mathrm{Vir}$, $\beta\gamma$ \\
$\mathfrak{sl}_3$ (conj.) & $1-3x-x^2$ & $\frac{-3\pm\sqrt{13}}{2}$ & $\widehat{\mathfrak{sl}}_3$, $\mathcal{W}_3$ \\
abelian & $1$ (no branch) & --- & $\mathcal{H}$, $\psi$ \\
\bottomrule
\end{tabular}
\end{center}

\begin{remark}[Predicted families]
Conjecture~\ref{conj:non-simply-laced-discriminant} predicts additional DS families:
\begin{itemize}
\item $\mathfrak{sl}_4$ family: $\widehat{\mathfrak{sl}}_4$ and $\mathcal{W}_4$, sharing a degree-$3$ DS-invariant discriminant (rank~$3$ plus one growth pole).  Growth rate $15^n = (\dim\mathfrak{sl}_4)^n$.
\item $G_2$ family: $\widehat{G}_2$ and $\mathcal{W}(G_2)$.  Growth rate $14^n$.  The DS-invariant discriminant is predicted to have degree $\operatorname{rank}(G_2) + 1 = 3$.
\item $\mathfrak{sp}_4$ family: non-simply-laced.  $h^\vee = 3 \neq h = 4$.  The dual Coxeter discrepancy should manifest in the discriminant structure.
\end{itemize}
None of these have any bar cohomology data beyond $H^1 = \dim\mathfrak{g}$.
\end{remark}


\section{Growth rates and singularity analysis}
\label{sec:growth-rates}

The exponential growth rate of $\dim(\cA^!)_n$ is determined by the dominant singularity of the generating function.  By analytic combinatorics (Flajolet--Sedgewick~\cite{FlajoletSedgewick}), the growth is $\alpha^n \cdot n^{\beta}$ where $\alpha = 1/R$ ($R$ = radius of convergence) and the exponent~$\beta$ depends on the singularity type.

\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccll}
\toprule
\textbf{Algebra} & $\alpha$ & $\beta$ & \textbf{Singularity type} & \textbf{Status} \\
\midrule
$\mathcal{H}$, $\psi$ & --- & --- & essential (modular) & proved \\
$bc$ & $2$ & $0$ & rational pole & proved \\
$\beta\gamma$ & $3$ & $-1/2$ & $\Delta^{-1/2}$ (algebraic) & proved \\
$\widehat{\mathfrak{sl}}_2$ & $3$ & $-3/2$ & $\Delta^{1/2}$ (algebraic) & proved \\
$\mathrm{Vir}_c$ & $3$ & $-3/2$ & $\Delta^{1/2}$ (algebraic) & proved \\
$\widehat{\mathfrak{sl}}_3$ & $8$ & $0$ & rational pole & conjectured \\
$\mathcal{W}_3$ & $\frac{3+\sqrt{13}}{2}$ & $0$ & rational pole & conjectured \\
$Y(\mathfrak{sl}_2)$ & $3$ & $0$ & rational pole & conjectured \\
$\widehat{G}_2$ & $14$ & ? & predicted & unknown \\
\bottomrule
\end{tabular}
\end{center}

\emph{The dichotomy $\beta = -3/2$ vs.\ $\beta = 0$.}
The proved cases ($\widehat{\mathfrak{sl}}_2$, $\mathrm{Vir}$) have sub-exponential correction $n^{-3/2}$, characteristic of square-root algebraic singularities.  The conjectured cases ($\widehat{\mathfrak{sl}}_3$, $\mathcal{W}_3$, $Y(\mathfrak{sl}_2)$) have $\beta = 0$, characteristic of simple rational poles.  If confirmed, this would mean that the shift from rank~$1$ ($\mathfrak{sl}_2$) to rank~$2$ ($\mathfrak{sl}_3$) changes the analytic nature of the generating function from algebraic to rational --- a qualitative transition in combinatorial complexity.

\emph{Universality of the growth rate $3$.}
The number~$3 = \dim\mathfrak{sl}_2$ appears as the growth rate for $\widehat{\mathfrak{sl}}_2$, $\mathrm{Vir}$, $\beta\gamma$, \emph{and} conjecturally $Y(\mathfrak{sl}_2)$.  The first three share a DS orbit; the Yangian does not.  The coincidence $\alpha_{Y(\mathfrak{sl}_2)} = 3 = \dim\mathfrak{sl}_2$ for the Yangian is explained by the RTT presentation: the generating matrices are $2 \times 2$, giving a $4$-dimensional space of generators ($= 2^2$), but the growth is controlled by the $\mathfrak{sl}_2$ factor after modding out the center.


\section{The modular characteristic and genus expansion}
\label{sec:modular-characteristic}

The modular characteristic $\kappa(\cA)$ is a scalar invariant that controls all genus corrections (Theorem~\ref{thm:modular-characteristic}).  Its computation for each algebra gives the following table.

\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lll}
\toprule
\textbf{Algebra} & $\kappa(\cA)$ & \textbf{Complementary partner} \\
\midrule
Heisenberg $\mathcal{H}_k$ & $k$ & $\mathcal{H}_{-k}$ \quad ($\kappa + \kappa' = 0$) \\
$\widehat{\mathfrak{sl}}_{2,k}$ & $\frac{3(k+2)}{4}$ & $\widehat{\mathfrak{sl}}_{2,-k-4}$ \quad ($\kappa + \kappa' = 0$) \\
$\widehat{\mathfrak{sl}}_{3,k}$ & $\frac{4(k+3)}{3}$ & $\widehat{\mathfrak{sl}}_{3,-k-6}$ \quad ($\kappa + \kappa' = 0$) \\
$\mathrm{Vir}_c$ & $c/2$ & $\mathrm{Vir}_{26-c}$ \quad ($\kappa + \kappa' = 13$) \\
$\mathcal{W}_3$ (central charge $c$) & $5c/6$ & $\mathcal{W}_3^{100-c}$ \quad ($\kappa + \kappa' = 250/3$) \\
General $\widehat{\mathfrak{g}}_k$ & $\frac{(k+h^\vee)\dim\mathfrak{g}}{2h^\vee}$ & $\widehat{\mathfrak{g}}_{-k-2h^\vee}$ \quad ($\kappa + \kappa' = 0$) \\
\bottomrule
\end{tabular}
\end{center}

\begin{remark}[Complementary partner $\neq$ Koszul dual]\label{rem:complementary-vs-koszul-dual}
The \emph{complementary partner} $\cA'$ appearing in this table
(defined by $\kappa(\cA) + \kappa(\cA') = \text{const}$) is in
general \emph{not} the Koszul dual~$\cA^!$.
For Kac--Moody algebras the two notions coincide:
$\widehat{\mathfrak{g}}_{-k-2h^\vee}$ is both the complementary
partner and the Koszul dual.  For the Heisenberg algebra, however,
they differ: the complementary partner is $\mathcal{H}_{-k}$
(the same algebra at the opposite level), while the Koszul dual is
$\mathcal{H}_k^! = \mathrm{Sym}^{\mathrm{ch}}(V^*)$ --- a chiral
symmetric algebra, structurally different from any Heisenberg algebra
(Theorem~\ref{thm:frame-heisenberg-koszul-dual},
Remark~\ref{rem:frame-three-dualities}).
\end{remark}

\emph{The genus expansion formula.}
For any algebra with modular characteristic $\kappa$, the bivariate generating function in the genus variable~$x$ is:
\[
\sum_{g \geq 1} F_g(\cA)\, x^{2g}
= \kappa(\cA) \cdot \left(\frac{x/2}{\sin(x/2)} - 1\right).
\]
This is the product of an algebra-dependent scalar ($\kappa$) and a universal transcendental function ($\hat{A}(x) - 1$).  The universal function is generated by Bernoulli numbers; the algebra-dependent factor is a rational function of the level.

\emph{Critical level.}
At $k = -h^\vee$ (the critical level), $\kappa = 0$ and every genus correction vanishes.  This is the level at which the Feigin--Frenkel center $\mathfrak{z}(\widehat{\mathfrak{g}})$ appears, and the geometric Langlands correspondence operates.

\emph{Complementarity arithmetic.}
For Kac--Moody algebras, complementarity gives $\kappa + \kappa' = 0$ (exact cancellation under $k \mapsto -k - 2h^\vee$).  For W-algebras obtained by DS reduction, the complementarity sum is nonzero and equals a characteristic constant of the DS orbit: $13$ for $\mathrm{Vir}$ (= half the bosonic string central charge), $250/3$ for $\mathcal{W}_3$ (since $\kappa(\mathcal{W}_3) = 5c/6$, reflecting the two generators of weights $2$ and $3$ contributing $c/2 + c/3$, so $\kappa + \kappa' = 5c/6 + 5(100-c)/6 = 250/3$).


\section{q-Series and modular structures}
\label{sec:q-series}

Several generating functions in the theory are (quasi-)modular forms or have modular transformation properties.

\subsection{Dedekind eta and partition functions}

The genus-$1$ partition function of the Heisenberg algebra is $Z_1(\mathcal{H}_k | \tau) = 1/\eta(\tau)$, where $\eta(\tau) = q^{1/24}\prod_{n \geq 1}(1-q^n)$ and $q = e^{2\pi i \tau}$.  The coefficients of $1/\eta$ are partition numbers.  For Kac--Moody algebras,
\[
Z_1(\widehat{\mathfrak{sl}}_{2,k} | \tau)
= \frac{\chi(\mathfrak{sl}_2)}{\eta(\tau)^3}
\cdot \bigl(1 + (k+2) E_2(\tau) + O(E_4)\bigr),
\]
where $\eta^3$ reflects $\dim\mathfrak{sl}_2 = 3$ and the correction involves the quasi-modular Eisenstein series~$E_2$.

\subsection{Eisenstein series and the holomorphic anomaly}

The weight-$2$ quasi-modular Eisenstein series $E_2(\tau) = 1 - 24\sum_{n \geq 1}\sigma_1(n)q^n$ transforms as
\[
E_2\!\left(\frac{a\tau+b}{c\tau+d}\right) = (c\tau+d)^2 E_2(\tau) - \frac{6c(c\tau+d)}{\pi i}.
\]
The inhomogeneous term $-6c(c\tau+d)/(\pi i)$ is the genus-$1$ holomorphic anomaly of the chiral bar complex: it measures the failure of the fiberwise bar differential to be modular-invariant.  For $\widehat{\mathfrak{sl}}_{2,k}$, the genus-$1$ curvature $d_{\mathrm{fib}}^2 = \kappa \cdot \omega_1$ (Theorem~\ref{thm:sl2-genus1-curvature}) has $\tau$-dependence controlled by $E_2(\tau)$, with $\kappa = 3(k+2)/4$.

\subsection{Minimal model characters}

The characters of the Virasoro minimal models $M(p,q)$ are:
\[
\chi_{r,s}(\tau)
= \frac{q^{h_{r,s} - c/24}}{\eta(\tau)}
\sum_{n \in \mathbb{Z}}
\bigl(q^{pqn^2 + (pr-qs)n} - q^{pqn^2 + (pr+qs)n}\bigr),
\]
with $c = 1 - 6(p-q)^2/(pq)$ and $h_{r,s} = ((pr-qs)^2 - (p-q)^2)/(4pq)$.  For the Ising model ($c = 1/2$, i.e., $M(3,4)$), the characters are:
\[
\chi_{\mathbb{I}} = \tfrac{1}{2}\bigl(\sqrt{\theta_3/\eta} + \sqrt{\theta_4/\eta}\bigr),
\qquad
\chi_\sigma = \tfrac{1}{\sqrt{2}}\sqrt{\theta_2/\eta},
\qquad
\chi_\varepsilon = \tfrac{1}{2}\bigl(\sqrt{\theta_3/\eta} - \sqrt{\theta_4/\eta}\bigr),
\]
in terms of Jacobi theta functions.

\subsection{Lattice theta series}

For a positive-definite even lattice~$\Lambda$, the theta series $\Theta_\Lambda(\tau) = \sum_{\alpha \in \Lambda} q^{\langle\alpha,\alpha\rangle/2}$ is a modular form of weight $\mathrm{rank}(\Lambda)/2$ for a congruence subgroup.  The lattice vertex algebra $V_\Lambda$ has partition function $Z_1(V_\Lambda | \tau) = \Theta_\Lambda(\tau) / \eta(\tau)^{\mathrm{rank}(\Lambda)}$.


\section{Open problems and the computational frontier}
\label{sec:open-problems}

We organize the remaining computational challenges by estimated difficulty.

\subsection{Near-term targets (single new bar cohomology value)}

\begin{enumerate}[label=\textbf{NF-\arabic*.}, leftmargin=3em]
\item\label{nf:sl3-h4}
\emph{$\dim H^4(\barBgeom(\widehat{\mathfrak{sl}}_{3,k})) \stackrel{?}{=} 1352$.}
This is the single most informative computation on the frontier.  The value $1352$ would confirm the rational GF (Conjecture~\ref{conj:sl3-bar-gf}) and the shared discriminant with $\mathcal{W}_3$; any other value would refute the rational form and require reconsidering the algebraicity class.

\emph{Obstruction}: the computation requires the rank of a $24576 \times 786432$ matrix over $\mathbb{Q}$ (or a suitable finite field $\mathbb{F}_p$).  This is a $\sim 20$\,GB dense matrix, beyond naive methods but within reach of sparse or modular arithmetic.

\emph{Progress} (Computation~\ref{comp:sl3-casimir-decomp}):
the Casimir eigenspace decomposition of $\mathfrak{sl}_3^{\otimes 4}$ has been
computed, giving $9$ eigenspaces with multiplicities
$(8, 256, 400, 891, 1050, 768, 112, 486, 125)$
at eigenvalues $3C_2 = (0, 18, 36, 48, 72, 90, 108, 120, 144)$.
The CE bracket rank within each eigenspace is known
(total rank $456$), and the tensor algebra complex is verified exact.
The PBW approach (computing $\mathfrak{sl}_3$-invariants in
$S^4(\mathfrak{sl}_3[t^{-1}]t^{-1})$ and the $d_1$ differential)
remains a candidate path to $H^4$ without the full matrix rank,
though the convergence target requires care
(Remark~\ref{rem:pbw-convergence-target}).

Additional progress:
\begin{itemize}
\item
The Koszul dual dimensions from series inversion are
$(A^!)_n = [1, 8, 28, 140, 392, 2884, \allowbreak\ldots]$
with chiral excess $[0, 0, 0, 84, 322, \ldots]$
(Remark~\ref{rem:sl3-koszul-dual}).
All positive through degree~$7$.
\item
No simple quadratic relation space $R \subseteq V \otimes V$
reproduces $H^n$ beyond degree~$2$
(Computation~\ref{comp:sl3-koszul-dual-scan}): the closest
candidate gives $H^3 = 120 \neq 204$.
\item
The Euler characteristic obstruction
(Remark~\ref{rem:euler-chi-obstruction}) shows that neither
$\mathfrak{g}^{\otimes n} \otimes \mathrm{OS}^{n-1}$ (fails at
weight~$2$) nor $\bar{A}^{\otimes n} \otimes \mathrm{OS}^{n-1}$
(fails at weight~$3$) gives a chain complex
consistent with $H^n = [1, 8, 36, 204]$.  This is a chain-level
manifestation of the $R^{(1)}$ barrier.
\end{itemize}

\item\label{nf:w3-h5}
\emph{$\dim H^5(\barBgeom(\mathcal{W}_3^k)) \stackrel{?}{=} 171$.}
Confirms the $\mathcal{W}_3$ recurrence (Conjecture~\ref{conj:w3-algebraicity}).  The computation is smaller than~\ref{nf:sl3-h4} because $\mathcal{W}_3$ has only two generators (compared to $8$ for $\mathfrak{sl}_3$), but the composite-field OPE (involving the $\Lambda = {:}TT{:}$ composite) introduces double-pole Wick contractions that prevent naive reduction.

\item\label{nf:yangian-h4}
\emph{$\dim H^4(\barBgeom(Y(\mathfrak{sl}_2))) \stackrel{?}{=} 82$.}
Confirms the Yangian rationality (Conjecture~\ref{conj:yangian-bar-gf}).  The Yangian has $4$ weight-$1$ generators (the RTT matrix entries), giving chain groups of manageable size: $\dim\bar{B}^4 = 4^4 \cdot 6 = 1536$.  This is computationally accessible.
\end{enumerate}

\subsection{Medium-term challenges (new families)}

\begin{enumerate}[label=\textbf{MF-\arabic*.}, leftmargin=3em]
\item \emph{$\widehat{G}_{2,k}$ bar cohomology at degrees $2$ and~$3$.}
The first genuinely non-simply-laced computation.  The chain groups have size $14^2 \cdot 1 = 196$ at degree~$2$ and $14^3 \cdot 2 = 5488$ at degree~$3$.  The degree-$2$ value is feasible; degree-$3$ requires the full $G_2$ structure constants (which involve the non-trivially-normalized short roots).

\item \emph{$\widehat{\mathfrak{sl}}_4$ through degree~$3$.}
With $\dim\mathfrak{sl}_4 = 15$, the chain groups are $15, 225, 6750$.  Three data points would determine the unique rational GF of degree $\operatorname{rank} + 1 = 4$ (if the rank-plus-one pattern holds), and would test whether the DS-invariant discriminant is a cubic polynomial.

\item \emph{Combinatorial model for $\widehat{\mathfrak{sl}}_2$.}
The Virasoro algebra has an explicit Motzkin path model (Theorem~\ref{thm:motzkin-path-model}).  An analogous model for $\widehat{\mathfrak{sl}}_2$ --- giving a bijection between $H^n(\barBgeom(\widehat{\mathfrak{sl}}_2))$ and a family of $R(n+3)$ combinatorial objects --- would illuminate the representation-theoretic meaning of the Riordan numbers.  Candidates: non-crossing partitions without singletons on $\{1, \ldots, n+3\}$; restricted lattice paths with three step types and a non-touching constraint.
\end{enumerate}

\subsection{Long-range problems}

\begin{enumerate}[label=\textbf{LR-\arabic*.}, leftmargin=3em]
\item \emph{Intrinsic construction of the Kodaira--Spencer operator.}
Conjecture~\ref{conj:discriminant-ks-operator} predicts a rank-$(\operatorname{rank}\mathfrak{g}+1)$ transfer operator $\mathrm{KS}_{\mathfrak{g}}$ whose characteristic polynomial recovers the discriminant.  An intrinsic construction (from the Casimir operators on the bar complex, without first computing the Hilbert series) would reduce the bar cohomology computation to a finite-dimensional eigenvalue problem.

\item \emph{Uniformization of the algebraic hierarchy.}
Is there a structural reason why rank-$1$ algebras have algebraic (degree~$2$) bar GFs while rank-$2$ algebras have rational GFs?  A possible framework: the Picard--Fuchs D-module of the bar GF has holonomic rank $\operatorname{rank}\mathfrak{g} + 1$; for rank~$1$ this is a second-order Fuchsian ODE (with algebraic solutions), while for rank~$2$ it is third-order (and the solution space may contain only rational functions if the monodromy is trivial).

\item \emph{Non-simply-laced discriminant structure.}
For non-simply-laced $\mathfrak{g}$, the DS reduction $\widehat{\mathfrak{g}}_k \twoheadrightarrow \mathcal{W}^k(\mathfrak{g})$ involves the dual Coxeter number $h^\vee \neq h$.  The discriminant should reflect this discrepancy.  For $B_2 = \mathfrak{sp}_4$: $h = 4$, $h^\vee = 3$, $\dim = 10$.  Does $\Delta_{\mathfrak{sp}_4}$ factor over $\mathbb{Q}(\sqrt{d})$ for some discriminant~$d$ involving both~$h$ and~$h^\vee$?

\item \emph{Periodicity and the Coxeter number.}
The Kac--Moody periodicity theorem gives period $2h$ for $\widehat{\mathfrak{sl}}_2$ (the $E_2$-page has period~$4$ in conformal weight).  Whether this periodicity manifests as a functional equation for the bar GF --- of the form $P(x) = \text{rational} + x^{2h} P(x)$, analogous to a modular relation --- is unknown.

\item \emph{$W_\infty$ and infinite-rank limits.}
The MC4 tower $\mathcal{W}_N$ as $N \to \infty$ should converge to $W_{1+\infty}$.  The bar cohomology dimensions $\dim(\mathcal{W}_N^!)_n$ form a two-parameter array $(N, n)$.  Is there a closed-form bivariate generating function $\sum_{N,n} \dim(\mathcal{W}_N^!)_n\, t^N x^n$?  For fixed~$n$, the $N$-dependence is polynomial (the number of generators grows linearly in~$N$), so the bivariate GF should be rational in~$t$.
\end{enumerate}


\section{Computational verification results}
\label{sec:computational-verification}
\index{bar complex!computational verification}
\index{chiral bracket differential!rank computation}

We record the results of systematic computational verification of the bar
cohomology data.  The computations use two independent methods: direct rank
computation of the chiral bracket differential (with Orlik--Solomon forms),
and algebraic generating function fitting (rational and holonomic recurrence
detection).  All computations are implemented in the \texttt{compute/} module
and validated by an automated test suite.

\subsection{Chiral bracket rank verification for $\widehat{\mathfrak{sl}}_3$}
\label{subsec:chiral-bracket-verification}

The chiral bracket differential
$d_{\mathrm{bracket}}\colon \bar{B}^n(\widehat{\mathfrak{sl}}_3) \to
\bar{B}^{n-1}(\widehat{\mathfrak{sl}}_3)$
acts on the full bar chain groups
$\bar{B}^n = \mathfrak{g}^{\otimes n} \otimes \mathrm{OS}^{n-1}(n)$,
where $\mathrm{OS}^{n-1}(n)$ is the top-degree component of the
Orlik--Solomon algebra of $\mathrm{Conf}_n(\mathbb{C})$
with $\dim\mathrm{OS}^{n-1}(n) = (n-1)!$.

Two versions of the bracket differential were computed independently:
the Chevalley--Eilenberg (CE) bracket on $\mathfrak{g}^{\otimes n}$
(ignoring the OS factor, i.e., treating all generators as living at the
same point), and the \emph{chiral} bracket incorporating the OS
residue maps $\operatorname{Res}_{D_{ij}}\colon
\mathrm{OS}^{n-1}(n) \to \mathrm{OS}^{n-2}(n-1)$
with signs $(-1)^{i+j}$.

\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{c|cc|cc|l}
\toprule
\textbf{Degree} & $\dim \bar{B}^n_{\mathrm{CE}}$ &
  $\dim \bar{B}^n_{\mathrm{chiral}}$ &
  $\mathrm{rk}_{\mathrm{CE}}$ & $\mathrm{rk}_{\mathrm{chiral}}$ &
  \textbf{Status} \\
\midrule
$2 \to 1$ & $64$ & $64$ & $8$ & $8$ & match \\
$3 \to 2$ & $512$ & $1024$ & $56$ & $63$ & \textbf{gap = 7} \\
$4 \to 3$ & $4096$ & $24576$ & $456$ & $1024$ & surjective \\
\bottomrule
\end{tabular}
\end{center}

The CE and chiral ranks agree at degree~$2 \to 1$ because
$\mathrm{OS}^0(2) = \mathbb{C}$ is one-dimensional.  At degree~$3 \to 2$,
the chiral bracket has rank~$63$ (matching
Computation~\ref{comp:sl3-modular-rank}), versus~$56$ for the
CE bracket.  The gap of~$7$ arises from the OS residue maps: the
seven additional kernel directions killed by the chiral
differential correspond to configurations where the collision
geometry (encoded by the Arnold relations
$\eta_{12} \wedge \eta_{23} + \eta_{23} \wedge \eta_{31} +
\eta_{31} \wedge \eta_{12} = 0$) enforces cancellations absent
in the pointwise CE complex.

At degree~$4 \to 3$, the chiral bracket is \emph{surjective}:
$\mathrm{rk} = 1024 = \dim \bar{B}^3$, consistent with the
Koszul property that bar cohomology is concentrated in low degrees.

\begin{remark}[CE vs.\ chiral: the string correction]
\label{rem:ce-vs-chiral}
\index{bar complex!CE vs chiral bracket}
The difference $\mathrm{rk}_{\mathrm{chiral}} - \mathrm{rk}_{\mathrm{CE}}
= 63 - 56 = 7$ at degree~$3$ measures the \emph{string correction}
to the bar differential: seven additional directions in
$\bar{B}^2$ become coboundaries when the full configuration-space
geometry is incorporated.  This difference is entirely due to the
non-trivial OS algebra structure at degree $\geq 3$, where the
Arnold relations begin to impose constraints.

The CE bracket is the $E_0$ page of the PBW spectral
sequence (ignoring the conformal weight grading), while the
chiral bracket incorporates the full Borcherds OPE data.  The
string correction measures the contribution of the higher spectral
sequence differentials at the level of total rank.
\end{remark}

\subsection{Near-rationality of the Virasoro bar sequence}
\label{subsec:virasoro-near-rationality}
\index{Virasoro algebra!near-rationality}
\index{bar complex!generating function!near-rationality}

The Virasoro bar cohomology dimensions $\dim(\mathrm{Vir}^!)_n = M(n+1) - M(n)$
(Motzkin differences, \S\ref{subsec:motzkin}) satisfy the algebraic GF
\begin{equation}\label{eq:virasoro-gf-algebraic}
P_{\mathrm{Vir}}(x) = \frac{4x}{(1 - x + \sqrt{1-2x-3x^2})^2},
\end{equation}
which is algebraic of degree~$2$ over $\mathbb{Q}(x)$ with discriminant
$\Delta = (1-3x)(1+x)$.  The generating function is \emph{not} rational.

However, automated recurrence detection reveals a striking numerical
coincidence: the constant-coefficient linear recurrence
\begin{equation}\label{eq:virasoro-spurious-recurrence}
a_k = 4\,a_{k-1} - 2\,a_{k-2} - 4\,a_{k-3}
\end{equation}
fits the Virasoro bar dimensions \emph{exactly} through degree~$8$:

\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|cccccccccc}
$n$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
\hline
actual & 1 & 2 & 5 & 12 & 30 & 76 & 196 & 512 & 1353 & 3610 \\
recurrence & --- & --- & --- & 12 & 30 & 76 & 196 & 512 & \textbf{1352} & \textbf{3604}
\end{tabular}
\end{center}

The recurrence~\eqref{eq:virasoro-spurious-recurrence} predicts $a_9 = 1352$,
while the true value is $M(10) - M(9) = 2188 - 835 = 1353$.  The discrepancy
is~$1$.  At degree~$10$, the error grows to~$6$; at degree~$11$, to~$27$.

This near-rationality is non-trivial: the spurious recurrence satisfies
$5$ overdetermined equations ($a_4$ through $a_8$, each being a
linear constraint on the $3$ unknowns $c_1, c_2, c_3$), then
fails at the $6$th.  The characteristic polynomial
$t^3 - 4t^2 + 2t + 4 = (t-2)(t^2 - 2t - 2)$ has roots
$2$ and $1 \pm \sqrt{3}$.  The dominant root $2$ accounts for the
rough exponential growth $\sim 2^n$, but the true growth rate is~$3^n$
(from the algebraic GF's singularity at $x = 1/3$).

\begin{proposition}[Pad\'e matching for the Virasoro bar sequence; \ClaimStatusProvedHere]
\label{prop:virasoro-pade}
\index{Virasoro algebra!Pad\'e approximation}
The depth-$3$ constant-coefficient
recurrence~\eqref{eq:virasoro-spurious-recurrence} is the $[3/3]$
Pad\'e approximant to the Motzkin difference sequence.  Exact rational
arithmetic computation of the $[q/q]$ diagonal Pad\'e approximant for
$q = 1, \ldots, 18$ reveals a period-$6$ structure:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The $[q/q]$ Pad\'e approximant \emph{does not exist}
  \textup{(}the Hankel determinant vanishes\textup{)} when
  $q \equiv 4$ or $5 \pmod{6}$.
\item When the Pad\'e approximant exists, it matches the Taylor
  coefficients of $P_{\mathrm{Vir}}(x)$ through degree exactly
  \begin{equation}\label{eq:pade-matching-formula}
    m(q) = 2q + 2 \cdot \mathbf{1}_{q \equiv 3 \pmod{6}}.
  \end{equation}
\item The error at the first mismatch is always exactly~$1$:
  $a_{m(q)+1} - a_{m(q)+1}^{\text{Pad\'e}} = 1$.
\end{enumerate}
In particular, the excess matching beyond the guaranteed $2q$ terms is
$O(1)$, bounded by~$2$---a stronger conclusion than the originally
conjectured $O(\sqrt{q})$.
\end{proposition}

\begin{proof}
Direct computation in exact rational arithmetic.  For each admissible
$q \leq 18$ (i.e., $q \not\equiv 4, 5 \pmod{6}$), one solves the
$q \times q$ Hankel system for the Pad\'e denominator, extracts the
linear recurrence, and compares with the Motzkin differences $M(n+1) -
M(n)$.  The computation verifies: $q = 3, 9, 15$ give excess $2$; $q
= 1, 2, 6, 7, 8, 12, 13, 14, 18$ give excess $0$; $q = 4, 5, 10,
11, 16, 17$ yield a singular Hankel matrix.  In all non-singular
cases, the first mismatch has error exactly~$1$.  The computation
covers three complete periods of the claimed $6$-periodicity.
\end{proof}

\begin{conjecture}[Period-\texorpdfstring{$6$}{6} Pad\'e structure; \ClaimStatusConjectured]
\label{conj:virasoro-pade-periodic}
\index{Virasoro algebra!Pad\'e approximation!periodicity}
The period-$6$ pattern of
Proposition~\textup{\ref{prop:virasoro-pade}} persists for all
$q \geq 1$: the $[q/q]$ Pad\'e approximant exists if and only if
$q \not\equiv 4, 5 \pmod{6}$, in which case the matching
formula~\eqref{eq:pade-matching-formula} holds with unit error.  The
$6$-periodicity of Hankel singularities and excess matching is
governed by the degree-$2$ algebraic structure of $P_{\mathrm{Vir}}(x)$
and the mod-$6$ arithmetic of the Catalan--Motzkin decomposition
$M(n) = \sum_{k} \binom{n}{2k} C_k$.
\end{conjecture}

\emph{Computational consequence.}  The near-rationality means that
automated GF solvers applied to Virasoro data with $\leq 8$ terms
will find a spurious rational fit.  This does not occur with $\geq 9$
terms, where the verification step detects the failure.  The lesson
is general: \emph{any constant-coefficient recurrence hypothesis
for an algebraic sequence must be validated against sufficiently
many terms} --- specifically, beyond the Padé horizon.

\subsection{GF type classification}
\label{subsec:gf-type-classification}
\index{bar complex!generating function!classification}

The bar cohomology generating functions fall into a hierarchy of
algebraic complexity.  Automated analysis confirms and refines the
classification of \S\ref{sec:gf-hierarchy}:

\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{llll}
\toprule
\textbf{Algebra} & \textbf{GF type} & \textbf{Recurrence type} &
  \textbf{Status} \\
\midrule
$\mathcal{H}$, $\psi$ & transcendental & none (modular) & proved \\
$bc$ & rational & $a_n = 2a_{n-1} + 1$ & proved \\
$\beta\gamma$ & algebraic (deg 2) & holonomic (order 2, poly deg 1) & proved \\
$\widehat{\mathfrak{sl}}_2$ & algebraic (deg 2) & holonomic (order 2, poly deg 1) & proved \\
$\mathrm{Vir}_c$ & algebraic (deg 2) & holonomic (order 2, poly deg 1) & proved \\
$\widehat{\mathfrak{sl}}_3$ & rational (conj.) & constant (depth 3) & conjectured \\
$\mathcal{W}_3$ & rational (conj.) & constant (depth 3) & conjectured \\
$Y(\mathfrak{sl}_2)$ & rational (conj.) & constant (depth 2) & conjectured \\
\bottomrule
\end{tabular}
\end{center}

The proved algebras in the $\mathfrak{sl}_2$ family all have
\emph{holonomic} recurrences --- linear recurrences with
\emph{polynomial} coefficients in~$n$ --- reflecting the algebraic
degree~$2$ of their generating functions.  The conjectured algebras
in the $\mathfrak{sl}_3$ family have constant-coefficient recurrences,
reflecting rationality.

\emph{The algebraic--rational transition.}
The qualitative shift from algebraic (degree~$2$) to rational when passing
from rank~$1$ ($\mathfrak{sl}_2$) to rank~$2$ ($\mathfrak{sl}_3$) is the
central mystery of the combinatorial frontier.  If the rank-plus-one pattern
(\S\ref{subsec:gf-sl3-family}) holds, then $\widehat{\mathfrak{sl}}_N$
for all $N \geq 3$ should have rational bar GFs, with the $\mathfrak{sl}_2$
family being the sole algebraic exception.  The PBW spectral sequence
provides a heuristic: for rank~$1$, the single Casimir operator gives
a depth-$2$ recurrence with polynomial coefficients (because the
invariant subalgebra $S^*(\mathfrak{g}[t^{-1}]t^{-1})^{\mathfrak{g}}$ has a
single generator); for rank~$\geq 2$, the multiple Casimir operators
interact to produce a deeper recurrence whose polynomial coefficients
may ``linearize'' (become constant) due to cancellations among the
Casimir eigenvalues on different weight spaces.

\subsection{Updated frontier targets}
\label{subsec:updated-frontier}

Based on the computational verification, we refine the obstruction analysis
for the near-term targets of \S\ref{sec:open-problems}.

\begin{enumerate}[label=\textbf{NF-\arabic*$'$.}, leftmargin=3em]
\item \emph{$\dim H^4(\barBgeom(\widehat{\mathfrak{sl}}_{3,k}))
\stackrel{?}{=} 1352$.}
The chiral bracket differential at degree~$4 \to 3$ has been verified
to be surjective (rank~$1024 = \dim \bar{B}^3$).
This means $\dim \ker(d^{4 \to 3}) = 24576 - 1024 = 23552$.
The value $H^4 = 1352$ would then require
$\dim \operatorname{im}(d^{5 \to 4}) = 23552 - 1352 = 22200$.
The degree-$5$ chain group has dimension
$\bar{B}^5 = 8^5 \cdot 4! = 786432$.
The rank computation of the $786432 \times 24576$ differential matrix
is the bottleneck.  Over $\mathbb{F}_p$ for a suitable prime $p > 3$,
this requires $\sim 786432 \times 24576 \approx 1.93 \times 10^{10}$
field operations, feasible on modern hardware in hours.

\item \emph{$\dim H^5(\barBgeom(\mathcal{W}_3^k))
\stackrel{?}{=} 171$.}
The $\mathcal{W}_3$ bar complex has generators $T$ (weight~$2$) and
$W$ (weight~$3$), with the composite field $\Lambda = {:}TT{:} -
\tfrac{3}{10}\partial^2 T$ appearing in the $W \times W$ OPE.
The degree-$5$ chain group is smaller than for $\mathfrak{sl}_3$
(only $2$ generators vs.~$8$), but the sixth-order pole in the
$W \times W$ OPE introduces non-trivial complications.
A full rank computation requires extending the \texttt{w3\_bar.py}
module to degree~$5$.

\item \emph{Alternative approach: PBW spectral sequence at degree~$4$.}
Rather than computing the full chiral bar differential, one can
attempt the PBW spectral sequence.  For $\widehat{\mathfrak{sl}}_3$,
the $E_1^{p,0}$ page at total degree $p = 4$ requires enumerating
the $\mathfrak{sl}_3$-invariants in
$S^4(\mathfrak{sl}_3[t^{-1}]t^{-1})$, which involves the two Casimir
invariants (degrees $2$ and $3$) and their products.  The space of
quartic invariants has the form
\[
\operatorname{Inv}^4 = S^2(C_2) \oplus C_2 \cdot C_3 \oplus S^4_0,
\]
where $C_2$ is the quadratic Casimir, $C_3$ the cubic Casimir,
and $S^4_0$ the ``new'' invariants at degree~$4$ (if any).
Computing $\dim S^4_0$ and the $d_1$ differential on these invariants
would yield $H^4$ without the large matrix rank computation.
\end{enumerate}

\subsection{Yangian $Y(\mathfrak{sl}_2)$ consistency verification}
\label{subsec:yangian-h4-verification}
\index{Yangian!bar cohomology!verification}
\index{bar complex!generating function!Yangian}

The conjectured Yangian bar generating function
(Conjecture~\ref{conj:yangian-bar-gf})
\begin{equation}\label{eq:yangian-gf-appendix}
P_{Y(\mathfrak{sl}_2)}(x) = \frac{1 - 3x^2}{(1-x)(1-3x)}
\end{equation}
predicts $\dim H^n = 3^n + 1$ for $n \geq 1$, with depth-$2$ recurrence
$a(n) = 4\,a(n{-}1) - 3\,a(n{-}2)$ for $n \geq 3$.  Seven independent
consistency checks were performed computationally:

\begin{enumerate}[label=(\roman*)]
\item \emph{Recurrence consistency.}
The denominator $D(x) = (1-x)(1-3x) = 1 - 4x + 3x^2$
and numerator $N(x) = 1 - 3x^2$ satisfy $D \cdot P = N$
through degree~$10$.  The recurrence reproduces $H^1 = 4$,
$H^2 = 10$, $H^3 = 28$ and predicts $H^4 = 82$.

\item \emph{Koszul identity.}
The formal product $H_A(t) \cdot H_{A^!}(-t) = 1$
with $H_A(t) = \sum (3^n + 1)\,t^n$ yields
Koszul dual dimensions
\[
H_{A^!}(t) = \frac{1 + 4t + 3t^2}{1 - 3t^2},
\]
with coefficients $1, 4, 6, 12, 18, 36, 54, 108, \ldots$ ---
positive integers through degree~$10$.  The closed form
$(A^!)_{2k} = 2 \cdot 3^k$, $(A^!)_{2k+1} = 4 \cdot 3^k$
is consistent with the representation theory of
$U_q(\mathfrak{sl}_2)$, the conjectured $E_1$-Koszul dual.

\item \emph{K\"unneth decomposition.}
The embedding $\mathfrak{gl}_2 = \mathfrak{sl}_2 \times
\mathfrak{gl}_1 \hookrightarrow Y(\mathfrak{sl}_2)$
gives a K\"unneth lower bound $H^n(\mathfrak{gl}_2) = \sum_{i+j=n}
R(i+3)\,p(j-2)$, where $R$ are Riordan numbers and $p$
partition numbers.  This matches $H^n(Y(\mathfrak{sl}_2))$
at degrees $n \leq 2$ (Serre correction zero) and underestimates
by $3, 20, 87$ at degrees $3, 4, 5$ respectively.  The Serre
corrections are the contribution of the Yangian's additional
(RTT-type) relations beyond the Lie algebra structure.

\item \emph{Rank cascade.}
With $4$ generators (RTT matrix entries), the chain groups
$\dim \bar{B}^n = 4^n \cdot (n-1)!$ give chain dimensions
$4, 16, 128, 1536, 24576$ and differential ranks
$0, 0, 6, 94, 1360$ (all non-negative and bounded above by
$\min(\dim \bar{B}^{n-1}, \dim \bar{B}^n)$).

\item \emph{Growth rate.}
The ratio $a(n)/a(n{-}1)$ converges to $3 = \dim\mathfrak{sl}_2$,
confirming that the growth rate saturates the general bound
$\dim\mathfrak{g}$ (Corollary~\ref{cor:growth-rate-dimg}).

\item \emph{Denominator factorization.}
$D(x) = (1-x)(1-3x)$ factors linearly over $\mathbb{Q}$
with roots $x = 1$ (from the $\mathfrak{gl}_1$ center)
and $x = 1/3$ (from the $\mathfrak{sl}_2$ factor),
consistent with the partial fraction decomposition
$P = -1 + 1/(1-x) + 1/(1-3x)$.

\item \emph{Euler characteristic.}
The evaluation $P(-1) = (1-3)/(2 \cdot 4) = -1/4$ gives a
formal Euler characteristic compatible with the alternating
dimension count.
\end{enumerate}

\noindent
All seven checks pass.  The conjectured value $H^4 = 82$
is \emph{strongly supported} by the consistency evidence,
but --- as with the $\mathfrak{sl}_3$ value $H^4 = 1352$ ---
not independently verified by direct chain-level computation.
The principal obstruction is the curvature differential
(double-pole OPE contributions), which is not yet implemented
for $E_1$-chiral algebras.

\emph{Distinction from $\widehat{\mathfrak{sl}}_3$.}
NF-3 is more accessible than NF-1 in two respects:
the chain groups are smaller ($\dim \bar{B}^4 = 1536$
vs.\ $24576$), and the $4$ RTT generators have a more
structured relation space than the $8$ adjoint generators
of $\mathfrak{sl}_3$.  However, the Yangian's non-commutative
($E_1$-chiral) structure means the bar differential includes
spectral parameter dependence absent in the KM case.


\subsection{$\mathcal{W}_3$ consistency verification (NF-2: $H^5 = 171$)}
\label{subsec:w3-h5-verification}

The $\mathcal{W}_3$ algebra has two strong generators $T$ (weight~$2$)
and $W$ (weight~$3$) and conjectured bar cohomology generating function
(Conjecture~\ref{conj:w3-bar-gf}):
\[
  P(x) = \frac{x(2 - 3x)}{(1-x)(1 - 3x - x^2)}, \qquad
  D(x) = 1 - 4x + 2x^2 + x^3.
\]
Known values: $H^1 = 2$, $H^2 = 5$, $H^3 = 16$, $H^4 = 52$.
The GF predicts $H^5 = 171$.

Seven independent consistency checks support this value:

\begin{enumerate}
\item \textbf{Recurrence consistency.}
  The relation $D(x) \cdot P(x) = N(x) = 2x - 3x^2$ gives
  the recurrence $a_k = 4a_{k-1} - 2a_{k-2} - a_{k-3}$
  for $k \ge 4$.  Applied to
  $a_1 = 2, a_2 = 5, a_3 = 16, a_4 = 52$,
  this yields $a_5 = 4 \cdot 52 - 2 \cdot 16 - 5 = 171$.

\item \textbf{Numerator verification.}
  The identity $D(x) \cdot P(x) = N(x)$ is verified through
  degree~$8$: the product $D \cdot P$ vanishes at $x^k$ for
  all $k > 2$, matching $N_k = 0$.

\item \textbf{Denominator factorisation.}
  $D(x) = (1-x)(1-3x-x^2)$.  The roots of $1-3x-x^2 = 0$
  are $x = (-3 \pm \sqrt{13})/2$, giving dominant growth rate
  $(3 + \sqrt{13})/2 \approx 3.303$.

\item \textbf{Growth rate.}
  The ratios $a_n / a_{n-1}$ converge to
  $(3 + \sqrt{13})/2$: values $2.5, 3.2, 3.25, 3.288$
  approach the limit from below.

\item \textbf{Drinfeld--Sokolov discriminant invariance.}
  The denominators of both the $\widehat{\mathfrak{sl}}_3$ and
  $\mathcal{W}_3$ bar GFs share the quadratic factor
  $1-3x-x^2$ with discriminant~$\Delta = 13$:
  \[
    D_{\mathfrak{sl}_3}(x) = (1-8x)(1-3x-x^2), \qquad
    D_{\mathcal{W}_3}(x) = (1-x)(1-3x-x^2).
  \]
  This shared discriminant is a DS invariant:
  $\mathcal{W}_3 = \mathrm{DS}(\widehat{\mathfrak{sl}}_3)$
  at the principal orbit, and the shared factor encodes
  the universal chiral correction from double Wick
  contractions.  The non-shared factors
  $(1-8x)$ and $(1-x)$ encode $\dim(\mathfrak{sl}_3) = 8$
  and the single $\mathcal{W}$-algebra Cartan direction,
  respectively.

\item \textbf{Virasoro subalgebra bound.}
  $\mathcal{W}_3 \supset \mathrm{Vir}$ (via~$T$), so
  $H^n(\bar{B}(\mathcal{W}_3)) \ge H^n(\bar{B}(\mathrm{Vir}))$.
  Verified: $2 \ge 1, \; 5 \ge 2, \; 16 \ge 5, \;
  52 \ge 12, \; 171 \ge 30$.

\item \textbf{Anti-Koszul check.}
  The standard Koszul dual Hilbert series
  $f_{\mathcal{A}^!}(t) = 1/f_{\mathcal{A}}(-t)$ has
  coefficients $1, 2, -1, 4, -7, \ldots$
  The appearance of $h_2 = -1 < 0$ confirms that
  $\mathcal{W}_3$ is \emph{not} classically Koszul,
  as expected from the sixth-order pole $W_{(5)}W = c/3$.
  (A classically Koszul algebra would give all-positive
  dual dimensions.)
\end{enumerate}

\noindent
All seven checks pass ($\mathtt{w3\_h5\_verification.py}$, 22 tests).
The conjectured value $H^5 = 171$ is strongly supported.
The principal obstruction to direct chain-level verification is the
degree-5 bar complex, where the $(n+1)$-fold tensor products of the
$\mathcal{W}_3$ vacuum module require the full composite-field OPE
including $\Lambda = {:}TT{:} - \tfrac{3}{10}\partial^2 T$.

\section{Summary of OEIS cross-references}
\label{sec:oeis}

\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lllp{5.5cm}}
\toprule
\textbf{OEIS} & \textbf{Sequence name} & \textbf{First terms} & \textbf{Role in the theory} \\
\midrule
A000041 & Partition numbers & 1,1,2,3,5,7,11 & Heisenberg/fermion bar cohomology \\
A000108 & Catalan numbers & 1,1,2,5,14,42 & Planar trees (HTT), associahedra \\
A001006 & Motzkin numbers & 1,1,2,4,9,21,51 & Virasoro bar $= M(n{+}1) - M(n)$ \\
A002026 & Motzkin differences & 0,1,2,5,12,30,76 & Virasoro bar cohomology directly \\
A005043 & Riordan numbers & 1,0,1,1,3,6,15,36 & $\widehat{\mathfrak{sl}}_2$ dims ($\neq R(5)$ at $n{=}2$) \\
A025565 & Central Delannoy (shifted) & 1,2,4,10,26,70 & $\beta\gamma$ bar cohomology \\
A132045 & $2^n - n + 1$ & 2,3,6,13,28,59 & $bc$ ghost bar cohomology \\
\bottomrule
\end{tabular}
\end{center}

\medskip

\noindent
The sequence $\dim H^n(\bar{B}(\mathcal{W}_3)) = 2, 5, 16, 52, \ldots$ does not appear in OEIS as of this writing.  The conjectured recurrence $a_k = 4a_{k-1} - 2a_{k-2} - a_{k-3}$ (from the rational GF $P(x) = x(2-3x)/((1-x)(1-3x-x^2))$; see \S\ref{subsec:w3-h5-verification}) gives $171, 564, 1862, 6149, \ldots$; this would be a new entry.  Similarly, the $\widehat{\mathfrak{sl}}_3$ sequence $8, 36, 204, \ldots$ (if confirmed through higher degrees) would be new.

\medskip

\emph{A naturality observation.}  The known bar cohomology sequences --- partition numbers, Riordan numbers, Motzkin numbers, central Delannoy numbers --- all belong to the class of lattice path counts (with varying step sets and boundary conditions).  This is not a coincidence: the PBW spectral sequence, which computes bar cohomology via iterated Lie algebra cohomology, can be reformulated as a lattice path enumeration problem, where each conformal weight level corresponds to a horizontal coordinate and each cohomological degree to a vertical coordinate.  The step set is determined by the OPE singularity structure: simple poles give rise to ``up'' and ``down'' steps, higher-order poles to ``flat'' steps, and the boundary condition (non-negativity of height) reflects the unitarity of the underlying vertex algebra.  A precise formulation of this lattice-path / bar-cohomology correspondence, extending the Motzkin path model of Theorem~\ref{thm:motzkin-path-model} to all Koszul chiral algebras, would constitute a significant structural advance.
