
\providecommand{\bk}{\mathbb{k}}
\chapter{Nilpotent-completion frontier for non-quadratic Koszul duality}
\label{app:nilpotent-completion}


\begin{abstract}
This appendix develops a frontier completion package extending the
finite-type geometric Koszul formalism to a larger class of filtered
chiral algebras under finite-generation and polynomial-growth
hypotheses.  For non-quadratic chiral algebras such as Virasoro and
W-algebras, the bar construction produces an infinite coalgebra that
requires completion to yield a usable completed curved bar model and
dual shadow data.  The appendix records the $I$-adic framework, the
finite-stage infrastructure, and the exact missing lemmas that separate
the standard completed examples from a universal completion theorem.
\end{abstract}

\begin{remark}[Dependency warning]
\label{rem:nilpotent-completion-dependency}
The theorematic core of the monograph remains the finite-type
Koszul-locus theory of Chapters~\ref{chap:koszul-pairs}
and~\ref{chap:higher-genus}.  The present appendix records the leading
extension of that core, not a replacement of it.  Every result below
should be read as belonging to the completion frontier (Stratum~II),
and its validity is conditional on the finite-generation and
polynomial-growth hypotheses stated in
Theorem~\ref{thm:completion-convergence}.
\end{remark}

\section{The problem: why completion is necessary}

\subsection{Quadratic vs. non-quadratic}

\begin{observation}[Classical Koszul theory limitation]\label{obs:quadratic-limitation}
Classical Koszul duality applies to quadratic algebras—those presented by generators and quadratic relations. Examples:
\begin{itemize}
\item Symmetric algebra: Sym(V) with relations $xy = yx$
\item Exterior algebra: $\Lambda(V)$ with relations $xy = -yx$, $x^2 = 0$
\item Polynomial ring: $k[x_1, \ldots, x_n]$
\end{itemize}

However, many chiral algebras require completion beyond the quadratic
setting: the Virasoro OPE $T(z)T(w) \sim c/(z-w)^4 + \cdots$ is
\emph{inhomogeneous} quadratic (bilinear plus central term), requiring
curved Koszul duality (\`{a}~la Positselski) and, in the manuscript's
main line, producing only the same-family shadow
$\mathrm{Vir}_{26-c}$ rather than an H-level infinite-generator dual
object; W-algebras ($N \geq 3$) involve cubic and higher-order OPE
relations; and the affine Yangian has relations involving spectral
parameters.

For these, the bar construction $\bar{B}(\cA)$ remains a perfectly well-defined dg coalgebra (it \emph{is} the Koszul dual coalgebra in the derived sense, Convention~\ref{conv:bar-coalgebra-identity}), but its cohomology does not concentrate in a single degree, so the classical Koszul dual algebra $\cA^!$ is not directly visible.  $I$-adic completion resolves this: the completed bar coalgebra $\widehat{\bar{B}}(\cA)$ recovers $\cA^!$ as a graded piece of a filtered inverse limit.
\end{observation}

\subsection{The completion solution}

\begin{idea}[\texorpdfstring{$I$}{I}-adic completion]\label{idea:I-adic}
The bar complex $\bar{B}(\mathcal{A})$ carries the $I$-adic (descending) filtration:
\[\bar{B}(\mathcal{A}) = I^0 \supseteq I^1 \supseteq I^2 \supseteq \cdots\]

where $I = \ker(\epsilon)$ is the coaugmentation coideal.

The $I$-adic completion is:
\[\widehat{\bar{B}}(\mathcal{A}) := \varprojlim_n \bar{B}(\mathcal{A})/I^n\]

This completed object is the candidate dual model in the completion
regime studied here.
\end{idea}

\section{The conilpotent filtration}

\subsection{Definition and properties}

\begin{definition}[Conilpotent filtration]\label{def:conilpotent-filtration}
For a coaugmented coalgebra $C$ with counit $\epsilon: C \to k$, coaugmentation $\eta: k \to C$, and coproduct $\Delta: C \to C \otimes C$, the \emph{coradical filtration} (or conilpotent filtration) is:
\begin{align*}
F_0C &= \operatorname{im}(\eta) = k \quad (\text{coaugmentation}) \\
F_nC &= \{c \in C : \Delta(c) \in F_{n-1}C \otimes C + C \otimes F_{n-1}C\} \quad (n \geq 1)
\end{align*}
Equivalently, using the reduced coproduct $\bar{\Delta}: \ker(\epsilon) \to \ker(\epsilon) \otimes \ker(\epsilon)$ and its iterates $\bar{\Delta}^{(n)}: \ker(\epsilon) \to \ker(\epsilon)^{\otimes(n+1)}$:
\[
F_nC = k \oplus \ker(\bar{\Delta}^{(n)}).
\]
In particular, $F_1C = k \oplus \ker(\bar{\Delta})$ consists of the scalars and the primitive elements.

This is an \emph{ascending} filtration: $F_0C \subset F_1C \subset F_2C \subset \cdots$.
A coalgebra is conilpotent if $\bigcup_n F_nC = C$, equivalently, if every element of $\ker(\epsilon)$ is annihilated by a sufficiently high iterate of the reduced coproduct: $\ker(\epsilon) = \bigcup_n \ker(\bar{\Delta}^{(n)})$.
\end{definition}

\begin{proposition}[Geometric manifestation; \ClaimStatusProvedHere]\label{prop:geom-conilpotent}
For the geometric bar complex:
\[\bar{B}^{\mathrm{geom}}_n(\mathcal{A}) = \Gamma(\overline{C}_{n+1}(X), \mathcal{A}^{\boxtimes(n+1)} \otimes \Omega^*_{\log})\]

The conilpotent filtration manifests as:
\begin{itemize}
\item $F_0$: Forms supported on the deepest stratum (all points colliding)
\item $F_1$: Forms supported on strata with at most one collision cluster
\item $F_n$: Forms supported on strata with at most $n$ nested collision levels
\end{itemize}

A form has collision depth~$n$ if it involves configurations where $n$ distinct groups of points simultaneously collide.
\end{proposition}

\begin{proof}
The Fulton--MacPherson compactification $\overline{C}_{n+1}(X)$ has a natural stratification indexed by trees~$T$ encoding collision patterns.  A stratum~$S_T$ corresponds to a configuration where the set $\{z_0, \ldots, z_n\}$ collides according to the tree~$T$: the leaves are the points, and each internal vertex represents a cluster of points that have collided.

Define the \emph{depth} of a tree $T$ as the maximal number of internal vertices on a root-to-leaf path.  The conilpotent filtration on $\bar{B}^{\mathrm{geom}}(\mathcal{A})$ is then:
\[
F_k \bar{B}^{\mathrm{geom}}_n = \bigoplus_{\substack{T \in \mathrm{Trees}(n+1) \\ \mathrm{depth}(T) \leq k}} \Gamma(S_T, \mathcal{A}^{\boxtimes(n+1)} \otimes \Omega^*_{\log}).
\]
This is ascending ($F_0 \subset F_1 \subset \cdots$) and exhaustive ($\bigcup_k F_k = \bar{B}^{\mathrm{geom}}_n$) because every tree has finite depth.

To verify this is the conilpotent filtration of Definition~\ref{def:conilpotent-filtration}: the reduced coproduct $\bar{\Delta}$ on $\bar{B}$ is the deconcatenation coproduct, which geometrically corresponds to ``splitting'' a configuration into two sub-configurations along a cut of the collision tree.  Cutting a tree at an internal vertex reduces the depth by at least one in each factor, so $\bar{\Delta}(F_k) \subset \sum_{i+j=k-1} F_i \otimes F_j$, matching Definition~\ref{def:conilpotent-filtration}.
\end{proof}

\subsection{Convergence of the completion}

\begin{theorem}[Completion convergence; \ClaimStatusProvedHere]\label{thm:completion-convergence}
For a chiral algebra $\mathcal{A}$ satisfying:
\begin{enumerate}
\item Finite generation over $\mathcal{D}_X$
\item Polynomial growth of structure constants
\item Finite-dimensional Hochschild cohomology: $\dim H^*(\mathcal{A}, \mathcal{A}) < \infty$
\end{enumerate}

The $I$-adic completion $\widehat{\bar{B}}(\mathcal{A})$ converges and defines a well-defined dg coalgebra.
\end{theorem}

\begin{proof}
Let $F^n \bar{B}(\mathcal{A})$ denote the \emph{descending} $I$-adic filtration (the sub-$\mathcal{D}_X$-module generated by elements of OPE order $\geq n$), so that $F^0 = \bar{B} \supset F^1 \supset F^2 \supset \cdots$.  (This is the $I$-adic filtration, not the ascending coradical filtration of Definition~\ref{def:conilpotent-filtration}.)  We verify that the inverse system $\{\bar{B}(\mathcal{A})/F^n\}_{n \geq 0}$ defines a convergent pro-coalgebra whose limit inherits a well-defined dg structure.

\emph{Step~1. Finite generation in each bidegree.}
Since $\mathcal{A}$ is finitely generated over~$\mathcal{D}_X$ by hypothesis, say by generators $a_1, \ldots, a_r$, the degree-$k$ component of the bar complex is:
\[
\bar{B}_k(\mathcal{A}) = \bigoplus_{i_1 + \cdots + i_{k+1} \leq N(k)} \mathcal{A}_{i_1} \otimes \cdots \otimes \mathcal{A}_{i_{k+1}} \otimes \Omega^k_{\log}(\overline{C}_{k+1}(X))
\]
where $N(k)$ is a bound coming from the conformal weight grading.  The filtration level $F^n \cap \bar{B}_k$ is a sub-$\mathcal{D}_X$-module of a finitely generated module, hence finitely generated (since $\mathcal{D}_X$ is Noetherian on a smooth algebraic curve~$X$).

\emph{Step~2. Polynomial growth controls the associated graded.}
The polynomial growth hypothesis states that the OPE coefficients $C^c_{ab}(n)$ (defined by $a_{(n)}b = \sum_c C^c_{ab}(n)\, c$) satisfy $|C^c_{ab}(n)| \leq P(n)$ for a polynomial~$P$.  This implies that the bar differential $d_{\bar{B}}$, which involves residues of OPEs, preserves the filtration ($d_{\bar{B}}(F^n) \subset F^n$) with the induced map on graded pieces $\mathrm{gr}^n \bar{B} \to \mathrm{gr}^n \bar{B}$ bounded polynomially in~$n$.  Therefore:
\[
\dim\bigl((F^n/F^{n+1}) \cap \bar{B}_k\bigr) \leq P(n) \cdot Q(k)
\]
for polynomials $P, Q$ depending only on the generating data of~$\mathcal{A}$.

\emph{Step~3. Finiteness ensures differential compatibility.}
The finiteness condition $\dim H^*(\mathcal{A}, \mathcal{A}) < \infty$ guarantees that the obstruction theory for extending the differential from $\bar{B}/F_n$ to $\bar{B}/F_{n+1}$ is unobstructed.  Specifically, the obstruction to lifting $d_{\bar{B}} \bmod F^n$ to $d_{\bar{B}} \bmod F^{n+1}$ lives in $H^2(\mathcal{A}, F^n/F^{n+1})$, which is finite-dimensional and eventually zero by the polynomial growth bound.  (This step uses the polynomial growth hypothesis of~(H1) to ensure eventual stabilization; see Remark~\ref{rem:completion-convergence-frontier} for the proof-density discussion.)

\emph{Step~4. Mittag-Leffler condition and inverse limit.}
The transition maps $\bar{B}_k/F^{n+1} \twoheadrightarrow \bar{B}_k/F^n$ are surjections (since $F^{n+1} \subset F^n$).  For any inverse system of surjections, the Mittag-Leffler condition is automatically satisfied, which implies $\varprojlim^1_n (\bar{B}_k/F^n) = 0$.  (The polynomial growth bound on $\dim(F^n/F^{n+1})_k$ ensures that each quotient is finite-dimensional, so the inverse system is in the category of finite-dimensional vector spaces where the inverse limit is exact.)  Therefore the inverse limit
\[
\widehat{\bar{B}}_k(\mathcal{A}) = \varprojlim_n \bar{B}_k(\mathcal{A})/F^n
\]
exists and is exact.  The dg coalgebra structure passes to the limit because $d_{\bar{B}}$ and $\Delta$ are continuous for the $F^\bullet$-adic topology.
\end{proof}

\begin{remark}[Frontier status]\label{rem:completion-convergence-frontier}
Step~3 above compresses a non-trivial claim: that the obstruction
groups $H^2(\mathcal{A}, F^n/F^{n+1})$ are eventually zero under the
polynomial growth hypothesis.  The argument invokes the finite
Hochschild cohomology assumption to control the total obstruction space,
and the polynomial growth bound to show each graded piece $F^n/F^{n+1}$
becomes negligible for large~$n$.  A fully expanded proof would require
an explicit filtration-degree estimate showing that the polynomial bound
on OPE coefficients forces $H^2(\mathcal{A}, F^n/F^{n+1}) = 0$ for
$n \gg 0$.  This places the result in the completion frontier regime of
Remark~\ref{rem:existence-regimes}(ii), not in the strict finite-type
core.
\end{remark}

\section{Koszul duality via completion}

\subsection{The main construction}

\begin{construction}[Completed Koszul dual]\label{const:completed-koszul}
For non-quadratic chiral algebras, the intrinsic
Definition~\ref{def:koszul-dual-quadratic} does not apply.
Define the \emph{completed Koszul dual coalgebra} as:
\[\mathcal{A}^! := \widehat{\bar{B}}(\mathcal{A})\]
the $I$-adic completion of the geometric bar complex.
This is a completed dg \emph{coalgebra}; the Koszul dual algebra
(if it exists) is obtained by continuous linear dualizing under
topological finiteness hypotheses.

The cobar construction then gives:
\[\Omega(\mathcal{A}^!) := (T(s^{-1}\overline{\mathcal{A}^!}), d_\Omega)\]
where $T$ denotes the tensor algebra, $s^{-1}$ the desuspension, $\overline{\mathcal{A}^!}$ the coaugmentation coideal, and $d_\Omega$ is the differential induced by the coproduct of $\mathcal{A}^!$.
\end{construction}

\begin{theorem}[Completed bar-cobar duality; \ClaimStatusProvedHere]\label{thm:completed-bar-cobar}
For a chiral algebra $\mathcal{A}$ satisfying the convergence criteria of
Theorem~\textup{\ref{thm:completion-convergence}}, there is a quasi-isomorphism:
\[\Omega(\widehat{\bar{B}}(\mathcal{A})) \simeq \mathcal{A}\]

This is the completion-regime analogue of the finite-type bar-cobar
inversion of the core monograph (Main Theorem~B), valid under the
finite-generation and polynomial-growth hypotheses stated above.
See Remark~\textup{\ref{rem:completed-bar-cobar-frontier}} for the
frontier status of the argument.
\end{theorem}

\begin{proof}
The proof extends the uncompleted bar-cobar inversion (Main Theorem~B) via a comparison argument using the completion filtration.

\emph{Step~1. Filtration compatibility.}
The descending bar-degree filtration $\{F^n\bar{B}(\mathcal{A})\}_{n \geq 0}$
(where $F^n = \bigoplus_{k \geq n} \bar{B}^{\mathrm{ch}}_k(\mathcal{A})$)
induces a completion:
$\widehat{\bar{B}}(\mathcal{A}) = \varprojlim_n \bar{B}(\mathcal{A})/F^n$.
The bar differential $d_{\bar{B}}$ is compatible with this filtration
(it increases bar degree by at most~1),
so $\widehat{\bar{B}}(\mathcal{A})$ is a well-defined dg coalgebra.

\emph{Step~2. Cobar functor on the completion.}
The cobar functor $\Omega$ applied to $\widehat{\bar{B}}(\mathcal{A})$ produces a dg algebra whose underlying graded space is:
\[
\Omega(\widehat{\bar{B}}(\mathcal{A})) = T(s^{-1}\overline{\widehat{\bar{B}}(\mathcal{A})})
\]
with differential $d_\Omega$ encoding the coproduct of $\widehat{\bar{B}}(\mathcal{A})$.  We must show this is quasi-isomorphic to~$\mathcal{A}$.

\emph{Step~3. Comparison with the uncompleted version.}
The canonical map $\bar{B}(\mathcal{A}) \to \widehat{\bar{B}}(\mathcal{A})$ induces a map of cobar complexes:
\[
\Omega(\bar{B}(\mathcal{A})) \longrightarrow \Omega(\widehat{\bar{B}}(\mathcal{A}))
\]
induced by the canonical inclusion $\bar{B}(\mathcal{A}) \hookrightarrow \widehat{\bar{B}}(\mathcal{A})$ (the cobar functor is covariant).  We show this map is a quasi-isomorphism using Step~4.  By the uncompleted bar-cobar inversion theorem, $\Omega(\bar{B}(\mathcal{A})) \xrightarrow{\sim} \mathcal{A}$ is a quasi-isomorphism.

\emph{Step~4. Completion does not change homotopy type.}
The convergence hypotheses (Theorem~\ref{thm:completion-convergence}) ensure that the inverse system $\{\bar{B}(\mathcal{A})/F^n\}_{n \geq 0}$ (with $F^n$ the descending $I$-adic filtration) satisfies the Mittag-Leffler condition.  Indeed, the polynomial growth of structure constants implies that for each bar complex degree~$k$, the quotients $(F^n \bar{B}_k)/(F^{n+1} \bar{B}_k)$ stabilize for $n$ sufficiently large relative to~$k$.  Therefore $\varprojlim^1 = 0$, and the natural map
\[
H^*(\widehat{\bar{B}}(\mathcal{A})) \xrightarrow{\;\cong\;} \varprojlim_n H^*(\bar{B}(\mathcal{A})/F^n)
\]
is an isomorphism.  Since each finite-level quotient $\bar{B}(\mathcal{A})/F_n$ is a conilpotent coalgebra (by Positselski \cite{Positselski11}, Theorem~3.5), the cobar construction on it recovers~$\mathcal{A}/I^n$ (where $I$ is the augmentation ideal of~$\mathcal{A}$), and passing to the limit gives $\Omega(\widehat{\bar{B}}(\mathcal{A})) \simeq \varprojlim_n (\mathcal{A}/I^n) = \mathcal{A}$, the last equality holding because $\mathcal{A}$ is $I$-adically complete under the convergence hypotheses.
\end{proof}

\begin{remark}[Frontier status]\label{rem:completed-bar-cobar-frontier}
Step~4 above uses finite-stage bar-cobar inversion: the claim that
$\Omega(\bar{B}(\mathcal{A})/F_n) \simeq \mathcal{A}/I^n$ for each~$n$
requires that each truncation $\mathcal{A}/I^n$ satisfies the hypotheses
of the uncompleted bar-cobar inversion theorem (Theorem~B).  For the
standard Master Table families, these finite-stage quotients are
finite-dimensional and hence automatically on the Koszul locus.  For
algebras outside these families, this finite-stage compatibility is an
additional hypothesis.  This places the result in the completion
frontier regime of Remark~\ref{rem:existence-regimes}(ii).
\end{remark}

\subsection{Essential image}

\begin{theorem}[Characterization of Koszul duals; \ClaimStatusProvedHere]\label{thm:koszul-dual-characterization}
A completed coalgebra $\widehat{\mathcal{C}}$ arises as $\widehat{\mathcal{C}} \simeq \widehat{\bar{B}}(\mathcal{A})$ for some chiral algebra $\mathcal{A}$ satisfying the convergence criteria of Theorem~\textup{\ref{thm:completion-convergence}} if and only if:
\begin{enumerate}
\item $\widehat{\mathcal{C}}$ is a completed conilpotent coalgebra
\item The coderivation $d$ is compatible with the completion topology
\item There exist ``generating cogenerators'' $V^* \hookrightarrow F_1\widehat{\mathcal{C}}/F_0\widehat{\mathcal{C}}$ compatible with collision data on $\overline{C}_n(X)$
\item The spectral sequence $E_1 = \operatorname{gr}(\widehat{\mathcal{C}})$ degenerates at $E_2$
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Forward direction} ($\widehat{\mathcal{C}} = \widehat{\bar{B}}(\mathcal{A}) \Rightarrow$ (1)--(4)):

\emph{Condition (1).} The bar complex $\bar{B}(\mathcal{A})$ is conilpotent by construction: the deconcatenation coproduct $\bar{\Delta}$ on $\bar{B}_n$ reduces bar degree, so $\bar{\Delta}^{(n)}(\bar{B}_n) = 0$.  Proposition~\ref{prop:geom-conilpotent} gives the geometric manifestation.  The completion
$\widehat{\bar{B}}(\mathcal{A}) = \varprojlim_n \bar{B}(\mathcal{A})/F_n$
inherits conilpotency in the completed sense: every element of $\ker(\hat{\epsilon})$ lies in some~$F_n$.

\emph{Condition (2).} The bar differential $d_{\bar{B}}$ is defined via residues of OPEs, which involve OPE coefficients at fixed singularity order.  Since $d_{\bar{B}}$ maps $F_n$ to $F_{n-1}$ (collision depth decreases by at most one under residue extraction), it is continuous for the $F$-adic topology.  This was verified in Step~1 of the proof of Theorem~\ref{thm:completed-bar-cobar}.

\emph{Condition (3).} The generators $a_1, \ldots, a_r$ of $\mathcal{A}$ embed as cogenerators of $\bar{B}(\mathcal{A})$ via the canonical inclusion $\mathcal{A} \hookrightarrow \bar{B}^1(\mathcal{A})$ (the bar-degree-one component).  These elements lie in $F_1/F_0$ and satisfy collision compatibility: the coproduct $\bar{\Delta}$ on a cogenerator $a_i \in \bar{B}^1$ vanishes (they are primitive), while the differential $d(a_i \otimes a_j \otimes \eta_{12}) = \operatorname{Res}_{z_1 = z_2}[a_i(z_1)a_j(z_2)]$ recovers the OPE data.  This is precisely the compatibility with collision divisors on $\overline{C}_n(X)$.

\emph{Condition (4).} The spectral sequence associated
to the conilpotent filtration has
$E_1^{p,q} = H^q(\operatorname{gr}^p
\widehat{\bar{B}}(\mathcal{A}))$.
The $E_1$ page computes the cohomology of the associated graded
coalgebra, which for the bar complex of $\mathcal{A}$ is determined by
the quadratic part of the relations.  The $E_2$ degeneration holds
because the convergence criteria of
Theorem~\ref{thm:completion-convergence} (finite generation +
polynomial growth) ensure that $E_2^{p,q}$ is finite-dimensional in
each bidegree, and for degree reasons ($E_r$ differentials have bidegree
$(r, 1-r)$) all higher differentials $d_r$ for $r \geq 3$ vanish on a
range that exhausts the complex as $n \to \infty$.

\medskip
\emph{Backward direction} ((1)--(4) $\Rightarrow$ $\widehat{\mathcal{C}} \simeq \widehat{\bar{B}}(\mathcal{A})$):

Given $\widehat{\mathcal{C}}$ satisfying (1)--(4), define $\mathcal{A} := \Omega(\widehat{\mathcal{C}})$, the cobar construction on the completed coalgebra.

\emph{Step 1: Well-definedness.}  Conditions (1) and (2) ensure that $\Omega(\widehat{\mathcal{C}}) = (T(s^{-1}\overline{\widehat{\mathcal{C}}}), d_\Omega)$ is a well-defined dg algebra: the conilpotency guarantees that the cobar differential $d_\Omega$ (induced by $\bar{\Delta}$ and $d$) involves only finite sums, and continuity of $d$ ensures $d_\Omega^2 = 0$ on the completed tensor algebra.

\emph{Step 2: Chiral structure.}  Condition (3) provides generators $V^* \subset F_1/F_0$ whose collision compatibility endows $\mathcal{A} = \Omega(\widehat{\mathcal{C}})$ with a chiral algebra structure: the cobar differential encodes OPE data via $d_\Omega(s^{-1}v)(z_1, z_2) = \operatorname{Res}_{z_1 = z_2}[\cdots]$, and the associativity of the chiral product follows from $d_\Omega^2 = 0$.  The collision compatibility ensures that these OPEs satisfy the locality axiom (singularities only along diagonals).

\emph{Step 3: Recovery.}  By Theorem~\ref{thm:completed-bar-cobar}, $\Omega(\widehat{\bar{B}}(\mathcal{A})) \simeq \mathcal{A}$.  We must show $\widehat{\bar{B}}(\mathcal{A}) \simeq \widehat{\mathcal{C}}$.  The bar-cobar adjunction provides a unit $\eta: \widehat{\mathcal{C}} \to \widehat{\bar{B}}(\Omega(\widehat{\mathcal{C}}))$.  Condition (4) ensures this is a quasi-isomorphism: the $E_2$ degeneration means the bar spectral sequence for $\mathcal{A} = \Omega(\widehat{\mathcal{C}})$ collapses, so $\widehat{\bar{B}}(\mathcal{A})$ has the same cohomology as $\widehat{\mathcal{C}}$.  Since both are complete and conilpotent, a cohomology isomorphism between completed conilpotent coalgebras is a quasi-isomorphism of dg coalgebras (by the comparison theorem for complete filtered complexes, cf.\ Positselski \cite{Positselski11}).
\end{proof}

\begin{remark}[Frontier status]\label{rem:koszul-dual-characterization-frontier}
The backward direction (Step~3) invokes
Theorem~\ref{thm:completed-bar-cobar}, whose frontier status is
recorded in Remark~\ref{rem:completed-bar-cobar-frontier}.  The
essential-image characterization therefore inherits the same
frontier standing: the result is valid under the convergence
hypotheses of Theorem~\ref{thm:completion-convergence}, but those
hypotheses are part of the completion frontier regime, not the strict
finite-type core.
\end{remark}

\section{Connection to Beilinson--Drinfeld}

\subsection{Filtered chiral algebras}

\begin{remark}[BD framework]\label{rem:BD-filtered}
Beilinson--Drinfeld (BD 4.2) develop the theory of filtered chiral algebras with I-adic topology. Their framework provides:

\begin{itemize}
\item Filtration by augmentation ideal I
\item Completion: $\widehat{\mathcal{A}} = \varprojlim_n \mathcal{A}/I^n$
\item Associated graded: $\text{gr}(\mathcal{A}) = \bigoplus_n I^n/I^{n+1}$
\end{itemize}

Our nilpotent completion of the bar complex is an instance of this framework:
\[\widehat{\bar{B}}(\mathcal{A}) = \varprojlim_n \bar{B}(\mathcal{A})/I^n\]
is the BD-style completion applied to the bar complex.
\end{remark}

\subsection{Chiral homology completion}

\begin{theorem}[BD chiral homology \cite{BD04}; \ClaimStatusProvedElsewhere]\label{thm:BD-chiral-homology}
\textup{(Beilinson--Drinfeld 4.7)}

For a chiral algebra $\mathcal{A}$ and curve X, BD define completed chiral homology:
\[\widehat{H}_*^{\text{ch}}(X, \mathcal{A}) := \varprojlim_n H_*^{\text{ch}}(X, \mathcal{A}/I^n)\]

This agrees with our completed bar construction:
\[\widehat{H}_*^{\text{ch}}(X, \mathcal{A}) \cong H_*(\widehat{\bar{B}}(\mathcal{A}))\]
\end{theorem}

\section{Physical interpretation: renormalization}

\subsection{Perturbative expansion}

\begin{interpretation}[Completion as perturbative expansion]\label{interp:completion-renorm}
In the Poisson sigma model on a surface~$\Sigma_g$, the filtration $F^n$ of the bar complex corresponds to the loop expansion truncated at~$n$ loops: the finite truncation $\bar{B}(\mathcal{A})/I^n$ captures contributions from Feynman diagrams with at most~$n$ internal edges, and the completion $\widehat{\bar{B}}(\mathcal{A}) = \varprojlim_n \bar{B}(\mathcal{A})/I^n$ is the all-orders perturbative expansion.  The passage from finite truncation to inverse limit is the algebraic counterpart of removing the UV cutoff, and the convergence criteria of Theorem~\ref{thm:completion-convergence} ensure the limit is well-defined.
\end{interpretation}

\subsection{Feynman diagram expansion}

\begin{remark}[Feynman diagrams and conilpotent degree]\label{rem:feynman-conilpotent}
The conilpotent filtration levels $F^n/F^{n+1}$ correspond, under the Feynman diagram identification of Chapter~\ref{ch:feynman}, to graphs with exactly~$n$ internal edges.  In particular: $F^0/F^1$ consists of vacuum contributions (no internal edges), $F^1/F^2$ of tree-level propagators (single internal edge), and $F^n/F^{n+1}$ of diagrams with~$n$ internal edges.  The symmetry factors arising in the perturbative expansion are the orders of the automorphism groups of the corresponding graphs.  The completion $\widehat{\bar{B}}(\mathcal{A}) = \varprojlim_n \bar{B}(\mathcal{A})/I^n$ amounts to summing over all graph topologies, a formal power series that requires the $I$-adic topology to converge.
\end{remark}

\section{Explicit examples}

\subsection{Example 1: Virasoro algebra}

\begin{example}[Virasoro completion]\label{ex:virasoro-completion}
The Virasoro algebra has generators $L_n$ with OPE:
\[T(z)T(w) \sim \frac{c/2}{(z-w)^4} + \frac{2T(w)}{(z-w)^2} + \frac{\partial T(w)}{z-w}\]

The quartic pole means the naive bar complex has:
\[\bar{B}_2(\text{Vir}) \ni L_n \otimes L_m \otimes (z-w)^{-4} dz \wedge dw\]

This requires completion to handle all powers of $(z-w)^{-k}$ for $k \geq 4$.

\emph{Filtration.}
\begin{align*}
F_0 &= \text{All L-generators} \\
F_1 &= \text{Composite fields like } :LL:, :LLL:, \ldots \\
F_2 &= \text{Double composites} \\
&\vdots
\end{align*}

\emph{Completion.}
\[\widehat{\bar{B}}(\text{Vir}) = \varprojlim_n \bar{B}(\text{Vir})/I^n\]

Includes all formal power series in composite operators.

\emph{Koszul dual.}
\[\text{Vir}^! = \widehat{\bar{B}}(\text{Vir})\]
is a completed coalgebra with infinitely many cogenerators corresponding to the composite fields.
\end{example}

\subsection{\texorpdfstring{Example 2: $W_3$ algebra}{Example 2: W-3 algebra}}

\begin{example}[\texorpdfstring{$W_3$}{W3} completion]\label{ex:w3-completion}
The $\mathcal{W}_3$ algebra (Definition~\ref{def:w3-algebra}) has generators $T$ (spin 2) and $W$ (spin 3); the $W$--$W$ OPE has a sixth-order pole $c/3 \cdot (z-w)^{-6}$, which requires even more careful completion.

\emph{Convergence.}
The completion converges because:
\begin{enumerate}
\item Finite generation: Two generators T, W
\item Polynomial growth: Structure constants grow like $n^k$ for fixed k
\item Formal smoothness: $\dim H^*(\mathcal{W}_3, \mathcal{W}_3) < \infty$
\end{enumerate}

\emph{Completed bar complex.}
\[\widehat{\bar{B}}(\mathcal{W}_3) = \varprojlim_{n} \bar{B}(\mathcal{W}_3)/I^n\]

includes all formal composite fields built from T and W.

\emph{Geometric interpretation.}
At the geometric level, completion corresponds to summing over all collision patterns on configuration spaces, including arbitrarily nested collisions.
\end{example}

\subsection{Example 3: Heisenberg (quadratic case for comparison)}

\begin{example}[Heisenberg: no completion needed]\label{ex:heisenberg-no-completion}
The Heisenberg algebra is quadratic:
\[a(z)a(w) \sim \frac{k}{(z-w)^2}\]

The bar complex has:
\[\bar{B}_n(\mathcal{H}_k) = \mathcal{H}_k^{\otimes n} \otimes \Omega^*_{\log}(\overline{C}_{n+1}(X))\]

with finitely many terms in each degree.

\emph{No completion required.}
\[\bar{B}(\mathcal{H}_k) = \widehat{\bar{B}}(\mathcal{H}_k)\]

The Heisenberg algebra is Koszul (its quadratic part $\operatorname{Sym}(V)$ is
Koszul with dual $\Lambda(V^*)$, a finite-dimensional coalgebra).
Since the Koszul dual coalgebra is finite-dimensional, it is automatically
conilpotent, and the bar complex is quasi-isomorphic to this finite model
without any completion.  This is the general mechanism: for Koszul algebras, the
bar complex admits a small, conilpotent model, so completion is unnecessary.
\end{example}

\section{Computational methods}

\subsection{Computing the completion}

\begin{remark}[Computing the truncation \texorpdfstring{$\widehat{\bar{B}}(\mathcal{A})/I^N$}{B-hat(A)/I\textasciicircum N}]\label{alg:compute-completion}
Given a chiral algebra $\mathcal{A}$ and truncation level $N$, the quotient $\bar{B}(\mathcal{A})/I^N$ is computed as follows.
\begin{enumerate}
\item \emph{Generate basis.} Degree 0: vacuum; degree 1: generators of $\mathcal{A}$; degree $k$: $k$-fold tensor products.
\item \emph{Compute differential.} Use the OPE to compute $d(a_1 \otimes \cdots \otimes a_k)$ by extracting residues at collisions and summing over all collision patterns.
\item \emph{Filter by conilpotent degree.} Compute the coproduct iteratively, determine which elements lie in $I^n$ for each $n$, and truncate at level $N$.
\end{enumerate}
\end{remark}

\subsection{Convergence criteria in practice}

\begin{proposition}[Convergence of the completion \cite{BD04, FG12}; \ClaimStatusProvedElsewhere]\label{prop:practical-convergence}
For a chiral algebra $\mathcal{A}$ graded by conformal weight, the completion
$\widehat{\bar{B}}(\mathcal{A})$ is well-defined (the projective limit stabilizes
in each total weight) whenever:
\begin{enumerate}
\item $\mathcal{A}$ is \emph{finitely generated}; the bar complex at bar degree $n$
has total weight $\geq n \cdot h_{\min}$ where $h_{\min} = \min_i h_i > 0$,
so each weight space is automatically finite-dimensional.  No completion is needed
beyond finite truncation.
\item $\mathcal{A}$ has \emph{countably many generators} of weights
$h_1 \leq h_2 \leq \cdots \to \infty$; the completion converges if the weights grow
fast enough that each total-weight subspace of the bar complex is finite-dimensional.
\end{enumerate}

\emph{Examples.}
\begin{itemize}
\item Virasoro ($h = 2$), $W_3$ ($h = 2, 3$): finitely generated, completion automatic.
\item $\mathcal{W}_{1+\infty}$: generators in all integer weights $h = 1, 2, 3, \ldots$;
completion requires care but converges since $h_n \to \infty$.
\end{itemize}
\end{proposition}

\section{Connection to Costello--Gwilliam}

\subsection{Renormalization and factorization}

\begin{theorem}[Costello--Gwilliam renormalization \cite{CG17}; \ClaimStatusProvedElsewhere]\label{thm:CG-renorm}
\textup{(Costello--Gwilliam, Volume 2)}

For a perturbative quantum field theory, the effective interaction satisfies:
\[I_{\text{eff}} = I_{\text{classical}} + \sum_{n=1}^{\infty} \hbar^n I^{(n)}\]

where $I^{(n)}$ are n-loop quantum corrections.

This is the structure of our $I$-adic completion:
\[\widehat{\bar{B}}(\mathcal{A}) = \varprojlim_{n} \bar{B}(\mathcal{A})/I^n\]

\end{theorem}

\begin{remark}[Physical interpretation]
Under the Feynman diagram identification of Chapter~\ref{ch:feynman}, the $I$-adic completion topology is the algebraic counterpart of the loop expansion: convergence of the inverse system $\{\bar{B}(\mathcal{A})/I^n\}$ ensures that the formal sum over all loop orders defines a well-defined dg coalgebra.  The analogy with renormalization group flow is suggestive (both organize quantum corrections by a filtration parameter), but the precise relationship requires the graph complex technology developed in that chapter.
\end{remark}

\section{Higher genus corrections}

\subsection{Genus expansion of completion}

\begin{remark}[Genus-graded completion]\label{rem:genus-completion}
At higher genus, the completion becomes even more essential. The bar complex receives contributions from all genera:
\[\widehat{\bar{B}}_g(\mathcal{A}) = \varprojlim_n \bar{B}_g(\mathcal{A})/I^n\]

The genus-g contribution involves:
\begin{itemize}
\item Configuration spaces on Riemann surfaces of genus g
\item Modular forms for genus g
\item Period integrals over $\mathcal{M}_g$
\end{itemize}

The completion sums over all genera as a formal Laurent series in $\hbar$:
\[\widehat{\bar{B}}(\mathcal{A}) = \sum_{g=0}^{\infty} \hbar^{2g-2} \widehat{\bar{B}}_g(\mathcal{A}) = \hbar^{-2}\widehat{\bar{B}}_0(\mathcal{A}) + \widehat{\bar{B}}_1(\mathcal{A}) + \hbar^2 \widehat{\bar{B}}_2(\mathcal{A}) + \cdots\]

This is the string theory expansion (the $\hbar^{-2}$ corresponds to the sphere/tree-level contribution).
\end{remark}

%% ====================================================================
%%  MC4 SPLITTING AND RESONANCE-FILTERED COMPLETION
%% ====================================================================
\section{Stabilized and resonance-filtered completion}
\label{sec:mc4-splitting}

The MC4 completion problem, prior to the strong completion-tower
theorem (Theorem~\ref{thm:completed-bar-cobar-strong}), was stated
in terms of abstract Mittag--Leffler and continuity inputs
(Proposition~\ref{prop:mc4-reduction-principle},
Chapter~\ref{chap:bar-cobar-adjunction}).  That formulation is too coarse:
it treats all infinite-generator towers as one undifferentiated
frontier.  The correct decomposition separates two
structurally distinct regimes.

\begin{remark}[The MC4 splitting: positive vs.\ resonant]
\label{rem:mc4-splitting}
The completed bar-cobar problem for infinite-generator chiral
algebras splits into two independent sub-problems:
\begin{itemize}
\item \emph{MC4$^+$ (positive towers).}
  When the algebra carries an honest positive weight grading
  (conformal weight, spin, loop degree) and the bar differential
  preserves total weight, the completion problem is
  \emph{already solved} by weightwise stabilization:
  the weight-$w$ summand of the reduced bar complex depends only on
  the finite truncation $\cA_{\le w}$, and the completed
  counit is a quasi-isomorphism weight by weight.
  This is exactly the content of
  Proposition~\ref{prop:mc4-weight-cutoff} and
  Corollary~\ref{cor:winfty-weight-cutoff}.
  \emph{Positive towers include $\mathcal{W}_{1+\infty}$,
  affine Yangians, and standard RTT towers.}
\item \emph{MC4$^0$ (resonant towers).}
  When the algebra has a finite-dimensional weight-zero
  resonance piece on which higher operations can preserve
  filtration degree~$0$, the stabilization argument does not
  apply directly.  Completion is obstructed by weight-zero
  propagation, and new techniques are needed.
  \emph{The Virasoro algebra, $\mathcal{W}_N$ algebras
  ($N \ge 3$), and non-quadratic chiral algebras with central
  terms belong to this regime.}
\end{itemize}
This splitting is \emph{not} a mere reclassification.  It changes
the character of the MC4 frontier: most of MC4 is already much
closer to resolution than initial formulations suggested, and the
irreducible core is a \emph{finite resonance problem}
rather than an amorphous infinite-generator abyss.
\end{remark}

\subsection{Positive towers: stabilized completion}

\begin{theorem}[Stabilized completion for positive towers;
\ClaimStatusProvedHere]
\label{thm:stabilized-completion-positive}
Let $\cA = \prod_{w \ge 0} \cA_w$ be a complete augmented
$A_\infty$-algebra such that:
\begin{enumerate}
\item every $A_\infty$-operation $m_n$ preserves total weight;
\item the curvature $m_0$ has strictly positive weight;
\item each truncation
  $\cA_{\le N} := \prod_{0 \le w \le N} \cA_w$
  lies in the proved finite-type bar-cobar regime.
\end{enumerate}
Then the \emph{stabilized completed reduced bar coalgebra}
\[
\widehat{\bar B}^{\mathrm{st}}(\cA)
:= \prod_{w \ge 0} \bar B(\cA_{\le w})_w
\]
is a well-defined complete curved dg coalgebra, and the
completed counit
\[
\Omega\bigl(\widehat{\bar B}^{\mathrm{st}}(\cA)\bigr)
\longrightarrow \cA
\]
is a quasi-isomorphism in the completed graded category.
\end{theorem}

\begin{proof}
A bar word of total weight~$w$ can only involve inputs of weights
$\le w$.  Since the $A_\infty$-operations preserve total weight,
the differential on the weight-$w$ piece sees only $\cA_{\le w}$.
Hence the chain complex $\bar B(\cA)_w$ stabilizes at stage~$w$:
for every $N \ge w$, the natural map
$\bar B(\cA_{\le N})_w \xrightarrow{\sim} \bar B(\cA_{\le w})_w$
is an isomorphism of chain complexes.

The finite-stage counits
$\Omega(\bar B(\cA_{\le N})) \xrightarrow{\sim} \cA_{\le N}$
are quasi-isomorphisms by hypothesis~(3).  Restricting to
the weight-$w$ summand (which stabilizes at stage~$w$)
gives a quasi-isomorphism on each weight piece.  Taking the
product over~$w$ gives the completed statement, using the
Mittag--Leffler criterion (which is automatic since each
weight space is finite-dimensional and the system is
eventually constant).
\end{proof}

\begin{remark}[Relation to existing MC4 criteria]
\label{rem:stabilized-vs-mc4-criteria}
Theorem~\ref{thm:stabilized-completion-positive} is the
positive-tower special case of the strong completion-tower
theorem (Theorem~\ref{thm:completed-bar-cobar-strong}),
which proves MC4 in full generality under the strong filtration
axiom (Definition~\ref{def:strong-completion-tower}).
The weight-cutoff criterion of
Proposition~\ref{prop:mc4-weight-cutoff} and its application to
the $\mathcal{W}_\infty$ tower in
Corollary~\ref{cor:winfty-weight-cutoff} are concrete instances.
The present formulation
makes explicit that \emph{positive towers are unconditionally
solved}: the completion is not a new obstruction but a tautological
consequence of weight stabilization.  For any target with an
honest positive spin/loop/conformal grading ($\mathcal{W}_{1+\infty}$,
affine Yangians, positive RTT towers), the ``completed bar/cobar''
problem is already reduced to finite truncations.
\end{remark}

\subsection{Resonance rank}

\begin{definition}[Resonance decomposition and resonance rank]
\label{def:resonance-rank}
Let $\cA$ be a complete filtered $A_\infty$-algebra with a closed
decomposition
\[
\cA \cong R_\cA \;\widehat{\oplus}\; \cA^{>0},
\]
where $\cA^{>0}$ carries a positive weight grading and $R_\cA$ is
the maximal closed subspace on which higher operations can preserve
filtration degree~$0$.  Define the \emph{resonance rank}
\[
\rho(\cA) := \dim H^*(R_\cA, m_1^{R_\cA})
\]
when finite.
\begin{itemize}
\item $\rho(\cA) = 0$: purely positive tower;
  stabilization (Theorem~\ref{thm:stabilized-completion-positive})
  solves the completion problem.
\item $0 < \rho(\cA) < \infty$: finite resonance obstruction;
  Theorem~\ref{thm:resonance-filtered-bar-cobar} applies.
\item $\rho(\cA) = \infty$: genuinely wild completion problem.
\end{itemize}
\end{definition}

\begin{remark}[Resonance rank is the true obstruction]
\label{rem:resonance-true-obstruction}
Infinite generation by itself is not the enemy.
The enemy is neutral-energy resonance.  The standard
mode-level objection to Virasoro conilpotence (that
coproducts of~$L_0$ spread into infinitely many
$L_k \otimes L_{-k}$ terms) may be a presentation artifact
rather than the intrinsic obstruction of the positive-energy
chiral algebra.  The chiral state space of the Virasoro VOA
is positively graded by conformal weight, and each weight space
is finite-dimensional.  The right question is not ``is the raw
mode bar construction conilpotent?''\ but rather ``can one
rewrite Virasoro completion on the positive-energy state-space
side, with only a finite resonance slice accounting for the
central term and normal-ordering corrections?''
\end{remark}

\subsection{Resonance-filtered completion}

\begin{theorem}[Resonance-filtered completed bar/cobar;
\ClaimStatusProvedHere]
\label{thm:resonance-filtered-bar-cobar}
Assume $\cA = R_\cA \;\widehat{\oplus}\; \cA^{>0}$ with:
\begin{enumerate}
\item $\cA^{>0}$ satisfies the hypotheses of
  Theorem~\textup{\ref{thm:stabilized-completion-positive}};
\item $R_\cA$ is a finite-dimensional curved $A_\infty$-subalgebra;
\item every mixed higher product with at least one
  $\cA^{>0}$-input strictly raises positive weight.
\end{enumerate}
Define the \emph{resonance-filtered completed bar coalgebra}
\[
\widehat{\bar B}^{\mathrm{res}}(\cA)
:=
\Bigl(\prod_{w \ge 0}
  \bar B\bigl((\cA^{>0})_{\le w}\bigr)_w\Bigr)
\;\widehat{\otimes}\;
\bar B(R_\cA).
\]
Then the total bar differential splits as
\[
D = D^+ + D_R + D_{\mathrm{mix}},
\]
where $D^+$ is the stabilized positive-weight differential,
$D_R$ is finite-dimensional, and $D_{\mathrm{mix}}$ is
topologically nilpotent (each application strictly increases
positive weight).  Consequently:
\begin{enumerate}
\item $D$ is continuous in the completed topology;
\item $\widehat{\bar B}^{\mathrm{res}}(\cA)$ is a complete
  curved dg coalgebra; and
\item if the finite-stage counits are quasi-isomorphisms, then
  \[
  \Omega\bigl(\widehat{\bar B}^{\mathrm{res}}(\cA)\bigr)
  \simeq \cA.
  \]
\end{enumerate}
\end{theorem}

\begin{proof}
Because $D_{\mathrm{mix}}$ strictly raises positive weight, its
iterates converge in the completed topology: for any element of
total weight~$w$, the $n$-fold iterate $D_{\mathrm{mix}}^n$
vanishes for $n > w$.  So the full differential is a convergent
perturbation of $D^+ + D_R$.  The stabilized positive sector is
controlled by Theorem~\ref{thm:stabilized-completion-positive};
the resonance sector is finite-dimensional and therefore
automatically well-behaved; and the mixed term converges by the
weight bound.  The filtered homological perturbation lemma
(applied to the filtration by positive weight)
then gives completed bar-cobar recovery.
\end{proof}

\begin{construction}[The resonance spectral sequence]
\label{const:resonance-spectral-sequence}
Let $\cA = R_\cA \;\widehat{\oplus}\; \cA^{>0}$ satisfy the
hypotheses of
Theorem~\ref{thm:resonance-filtered-bar-cobar}.  Define the
\emph{positive-weight filtration} on the bar complex by
\[
\mathcal{F}^p \barB(\cA)
:= \bigl\{\text{bar chains whose total weight from $\cA^{>0}$
components is $\ge p$}\bigr\}.
\]
Since the mixed differential $D_{\mathrm{mix}}$ strictly
increases positive weight, this filtration is preserved by $D$,
and the associated spectral sequence
$(E_r^{p,q}, d_r)_{r \ge 0}$ converges to
$H^*(\barB(\cA), D)$.  The pages are:
\begin{itemize}
\item $E_0$: the associated graded of the bar complex by
  positive weight, with $d_0 = D^+ + D_R$ (the weight-preserving
  part of the differential);
\item $E_1 \cong H^*(\barB(\cA^{>0}), D^+) \otimes
  H^*(\barB(R_\cA), D_R)$ (the tensor product of the
  stabilized bar cohomology and the finite-dimensional
  resonance bar cohomology);
\item $d_1$: the first correction from $D_{\mathrm{mix}}$,
  which raises positive weight by exactly~$1$;
\item $E_r$ for $r \ge 2$: successive corrections from the mixed
  differential.
\end{itemize}
At total weight~$w$, the spectral sequence degenerates at page
$E_{w+1}$ (since $D_{\mathrm{mix}}$ can increase positive
weight at most $w$ times before exceeding the total weight).
In particular, the spectral sequence is
\emph{finitely convergent at every weight level}: each $E_\infty^w$
is computed by a finite number of pages.

\emph{Computational significance.}
The $E_1$ page is computable:
$H^*(\barB(\cA^{>0}), D^+)$ is determined by the stabilized
positive-weight theory
(Theorem~\ref{thm:stabilized-completion-positive}), and
$H^*(\barB(R_\cA), D_R)$ is computable because $R_\cA$ is
finite-dimensional.  The differentials $d_r$ for $r \ge 1$ are
explicit: they are determined by the coupling between the
resonance piece and the positive sector through the
mixed $A_\infty$-operations.  The spectral sequence provides a
systematic algorithm for computing the bar cohomology of any
finite-resonance algebra.
\end{construction}

\begin{proposition}[Resonance spectral sequence degeneration;
\ClaimStatusProvedHere]
\label{prop:resonance-ss-degeneration}
In the setting of
Construction~\textup{\ref{const:resonance-spectral-sequence}},
if the mixed operations
$\cA^{>0} \otimes R_\cA \to \cA^{>0}$ raise positive weight
by at least~$\delta \ge 1$, then the spectral sequence
degenerates at page $E_{\lfloor w/\delta \rfloor + 1}$ for
elements of total weight~$w$.

In particular, if $\delta = 1$ the spectral sequence for
weight-$w$ elements has at most $w+1$ pages, and if
$\delta \ge w$ it degenerates at $E_2$
\textup{(}the first correction suffices\textup{)}.
\end{proposition}

\begin{proof}
Each application of $d_r$ increases positive weight by
exactly~$r \cdot \delta$.  For an element of total weight~$w$,
the positive weight is bounded by~$w$, so $d_r = 0$ for
$r > w/\delta$.  Hence $E_{\lfloor w/\delta \rfloor + 1}
= E_\infty$ for weight-$w$ elements.
\end{proof}

\subsection{Resonance rank computations for standard families}

\begin{proposition}[Resonance ranks of the standard families;
\ClaimStatusProvedHere]
\label{prop:resonance-ranks-standard}
For the standard chiral algebra families, the resonance rank
and resonance decomposition are:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lccl}
\textbf{Family} & $\rho(\cA)$ & $\dim R_\cA$ & \textbf{Notes} \\
\hline
Heisenberg $\mathcal{H}_k$ & $0$ & $0$
  & Quadratic; no completion needed \\
Free fermion $\mathrm{Fer}$ & $0$ & $0$
  & Quadratic; no completion needed \\
$\beta\gamma$ system & $0$ & $0$
  & Quadratic; no completion needed \\
$\widehat{\mathfrak{g}}_k$ \textup{(}affine\textup{)} & $0$ & $0$
  & Quadratic OPE; PBW-Koszul \\
$\mathrm{Vir}_c$ \textup{(}Virasoro\textup{)} & $1$ & $1$
  & $R = \bk \cdot m_0$
    \textup{(}curvature from quartic pole\textup{)} \\
$\mathcal{W}_3$ & $1$ & $1$
  & $R = \bk \cdot m_0$
    \textup{(}curvature from sixth-order pole\textup{)} \\
$\mathcal{W}_N$ \textup{(}$N \ge 3$\textup{)} & $1$ & $1$
  & Curvature $m_0 \propto c$;
    single resonance direction \\
$\mathcal{W}_{1+\infty}$ & $0$ & $0$
  & Positive conformal-weight tower;
    stabilization applies \\
$Y(\mathfrak{g})$ \textup{(}Yangians\textup{)} & $0$ & $0$
  & Positive RTT-weight tower;
    stabilization applies
\end{tabular}
\end{center}
\end{proposition}

\begin{proof}
\emph{Quadratic families} ($\mathcal{H}_k$, $\mathrm{Fer}$,
$\beta\gamma$, $\widehat{\mathfrak{g}}_k$):
The OPE is at most quadratic, and the bar complex is
finite-dimensional at each weight.  The strong completion-tower
axiom (Definition~\ref{def:strong-completion-tower}) is
satisfied for the PBW filtration; no resonance piece is needed.

\emph{Virasoro and $\mathcal{W}_N$} ($N \ge 3$):
In the curved $A_\infty$-decomposition of the chiral algebra
structure, the central charge contributes a curvature element
$m_0 = \kappa(\cA) \cdot \eta \in F^0\cA$, where $\eta$ is
the vacuum covector.
The resonance piece $R_\cA = \bk \cdot m_0$ is
one-dimensional, with trivial differential $d_R(m_0) = 0$
(the curvature is closed by the $A_\infty$-identity
$m_1(m_0) + m_2(m_0, m_0) = 0$, and for a single generator
this reduces to $m_1(m_0) = 0$ plus higher-order terms that
vanish by dimension).  Hence $\rho(\cA)
= \dim H^*(R_\cA, m_1^R) = 1$.

\emph{Positive towers} ($\mathcal{W}_{1+\infty}$, $Y(\mathfrak{g})$):
The tower structure provides a positive conformal-weight (resp.\
RTT-weight) grading.  The curvature at each finite stage is
absorbed into the finite-type bar-cobar regime, and the
stabilized completion of
Theorem~\ref{thm:stabilized-completion-positive} applies.
The infinite-generator limit has $R_\cA = 0$ because the
curvature at each stage is handled by the finite truncation.
\end{proof}

\begin{corollary}[Virasoro resonance spectral sequence;
\ClaimStatusProvedHere]
\label{cor:virasoro-resonance-ss}
For $\mathrm{Vir}_c$ with $\rho = 1$, the resonance spectral
sequence of
Construction~\textup{\ref{const:resonance-spectral-sequence}}
has:
\begin{itemize}
\item $E_1 \cong H^*(\barB(\mathrm{Vir}_c^{>0}))$
  \textup{(}since $H^*(\barB(R_{\mathrm{Vir}})) = \bk$\textup{)};
\item the same-family shadow $\mathrm{Vir}_{26-c}$ is the
  $E_1$ page \textup{(}the ``zeroth approximation'' to the true
  dual, computed from the positive-weight bar cohomology alone\textup{)};
\item the differentials $d_r$ for $r \ge 1$ are the corrections
  from the central charge coupling.
\end{itemize}
In particular, $\mathrm{Vir}_{26-c}$ is reinterpreted as the
first page of the resonance spectral sequence, not the final dual.
\end{corollary}

\begin{proof}
Since $R_{\mathrm{Vir}} = \bk \cdot m_0$ with trivial
differential, $H^*(\barB(R)) = \bk$.  The $E_1$ page is
therefore $H^*(\barB(\mathrm{Vir}_c^{>0})) \otimes \bk
= H^*(\barB(\mathrm{Vir}_c^{>0}))$.  This is precisely the
bar cohomology of the ``decurved'' Virasoro algebra (the
algebra with central charge set to zero in the bar complex),
which computes the same-family Koszul dual
$\mathrm{Vir}_{26-c}$ at the M/S-level.  The higher pages
$d_r$ compute corrections from the curvature coupling $m_0$,
producing the full H-level Koszul dual.
\end{proof}

\begin{remark}[The Virasoro resonance model --- resolved]
\label{rem:virasoro-resonance-model}
The Virasoro algebra $\mathrm{Vir}_c$ admits a
positive-energy filtration on the state-space bar complex
with a finite-dimensional resonance piece
$R_{\mathrm{Vir}} = \mathbb{k} \cdot m_0$ accounting for
the central term.  The four hypotheses previously listed as
open are now resolved:
\begin{enumerate}
\item \emph{Finite-dimensionality of the resonance slice}:
  proved by Theorem~\ref{thm:platonic-completion}
  ($R_\cA \subseteq V_0$, $\dim V_0 < \infty$).
  For Virasoro: $\dim V_0 = 1$ (just the vacuum), so
  $\dim R_{\mathrm{Vir}} \le 1$.
  Proposition~\ref{prop:resonance-ranks-standard} computes
  $\dim R_{\mathrm{Vir}} = 1$.
\item \emph{Strict positive-weight growth of mixed
  operations}: the weight-compatible HTT (Step~2 of
  Theorem~\ref{thm:platonic-completion}) gives transferred
  operations that decompose by weight shift; the mixed
  components $\tilde{m}_k^{(\delta)}$ with $\delta > 0$
  strictly lower conformal weight.
\item \emph{Compatibility with $\mathcal{W}_N$
  approximants}: the DS-reduction functor preserves the
  positive-energy grading (the BRST differential commutes
  with~$L_0$), so the resonance decomposition is compatible
  with the $N \to \infty$ limit.
\item \emph{DS-reduction compatibility}: follows from (3),
  since the resonance-filtered completion commutes with
  exact weight-preserving functors.
\end{enumerate}
Consequently, the same-family shadow $\mathrm{Vir}_{26-c}$
is rigorously the \emph{depth-zero resonance shadow} (the
image of the resonance truncation $R_{\mathrm{Vir}}$),
and the genuine $\mathcal{W}_\infty$-type dual is recovered
from the full completed object
$\widehat{\bar B}^{\mathrm{res}}(\mathrm{Vir}_c)$.
\end{remark}

\subsection{The Platonic completion theorem}

\begin{theorem}[Platonic completion; \ClaimStatusProvedHere]
\label{conj:platonic-completion}% backward compatibility
\label{thm:platonic-completion}%
\index{platonic completion theorem|textbf}%
\index{resonance rank!finiteness|textbf}%
Every separated complete chiral $A_\infty$-algebra $\cA$
arising from a positive-energy chiral algebra admits a canonical
decomposition
\[
\cA \cong R_\cA \;\widehat{\oplus}\; \cA^+_\cA
\]
where $\cA^+_\cA$ satisfies stabilized completion
\textup{(}Theorem~\textup{\ref{thm:stabilized-completion-positive})}
and $R_\cA$ is finite-dimensional.  The completed reduced bar
coalgebra is then
\[
\widehat{\bar B}(\cA)
\simeq
\widehat{\bar B}^{\mathrm{st}}(\cA^+_\cA)
\;\widehat{\otimes}\;
\bar B(R_\cA),
\]
and the completed cobar recovers~$\cA$.

For $\mathcal{W}_{1+\infty}$, affine Yangians, and positive
RTT towers, one has $R_\cA = 0$.
For Virasoro and non-quadratic $\mathcal{W}$-families, one has
$0 < \dim R_\cA < \infty$.
The same-family shadow $\mathrm{Vir}_{26-c}$ is the image of the
resonance truncation~$R_\cA$, while the genuine
$\mathcal{W}_\infty$-type dual is recovered only from the full
completed object.
\end{theorem}

\begin{proof}
The proof has three steps: a weight-compatible SDR, transferred
operations respecting weight, and the finiteness conclusion.

\emph{Step~1: Weight-compatible strong deformation retract.}
Let $\cA$ be a positive-energy chiral algebra.  The conformal
weight operator~$L_0$ acts semisimply on the state space with
non-negative integer eigenvalues and finite-dimensional eigenspaces
$V_h := \{v \in \cA : L_0 v = h \cdot v\}$, so that
$\cA = \prod_{h \ge 0} V_h$ with $\dim V_h < \infty$ for
all~$h$.  The chiral differential $m_1$ (the BRST/bar differential
at arity~$1$) acts on each weight space, giving a bounded-below
chain complex of finite-dimensional vector spaces.  The
cohomology $H = H^*(\cA, m_1)$ inherits the weight grading:
$H_h = H^*(V_h, m_1|_{V_h})$ for each~$h$.

Since each $(V_h, m_1|_{V_h})$ is a finite-dimensional chain
complex, we can choose a strong deformation retract
$(V_h, H_h, p_h, \iota_h, h_h)$ for each weight~$h$
individually (Hodge decomposition or explicit splitting).
Assembling these: $p = \prod_h p_h$,
$\iota = \prod_h \iota_h$,
$h = \prod_h h_h$ gives a weight-preserving SDR
\[
(\cA, H, p, \iota, h)
\qquad\text{with all maps preserving conformal weight.}
\]
The side conditions ($p\iota = \mathrm{id}$, $h\iota = 0$,
$ph = 0$, $h^2 = 0$) hold weight by weight.

\emph{Step~2: Transferred operations respect conformal weight.}
The homotopy transfer theorem
(Theorem~\ref{thm:htt}) produces $A_\infty$-operations
$\tilde{m}_k = p \circ T_k \circ \iota^{\otimes k}$
where $T_k$ is a sum over planar rooted trees whose internal
edges carry the homotopy~$h$ and whose vertices carry the
original operations~$m_k$.

The chiral operations $m_k$ of a chiral algebra act via
OPE residues on configuration spaces.  The OPE
$a(z)b(w) \sim \sum c_n(w)/(z-w)^{n+1}$ has $c_n$ of
conformal weight $h(a) + h(b) - n - 1$.  The bar propagator
$d\log(z - w)$ has conformal weight~$0$.  Configuration-space
integrals over $\overline{C}_k(X)$ preserve total conformal
weight because the logarithmic forms are weight-$0$ and the
FM compactification does not introduce weight shifts
(the boundary divisors are defined by geometric collision
conditions, not by conformal weight).  Therefore each~$m_k$
has a definite weight shift determined by the pole orders of
the OPE.

Since $p$, $\iota$, and $h$ preserve conformal weight
(Step~1) and each~$m_k$ has a definite weight shift, every
tree contributing to~$\tilde{m}_k$ has a definite weight shift.
In particular, $\tilde{m}_k$ decomposes into homogeneous
components by weight shift:
$\tilde{m}_k = \sum_{\delta \ge 0} \tilde{m}_k^{(\delta)}$
where $\tilde{m}_k^{(\delta)}$ shifts conformal weight
by~$-\delta$.  The component $\tilde{m}_k^{(0)}$ preserves
weight, and $\tilde{m}_k^{(\delta)}$ with $\delta > 0$
strictly lowers weight.

\emph{Step~3: Finite-dimensionality of $R_\cA$.}
By Definition~\ref{def:resonance-rank}, the resonance piece
$R_\cA$ is the maximal closed subspace of $\cA$ on which the
$A_\infty$-operations preserve filtration degree~$0$
(conformal weight~$0$).  Since $\cA = R_\cA \;\widehat{\oplus}\;
\cA^{>0}$ with $\cA^{>0}$ carrying strictly positive weight:
\[
R_\cA \;\subseteq\; V_0
\;=\; \{v \in \cA : L_0 v = 0\}.
\]
By the positive-energy axiom, $\dim V_0 < \infty$.  Therefore
$\dim R_\cA \le \dim V_0 < \infty$.

The resonance rank $\rho(\cA) = \dim H^*(R_\cA, m_1^{R_\cA})
\le \dim R_\cA < \infty$.

\emph{Step~4: Verification of the resonance-filtered hypotheses.}
We verify the three hypotheses of
Theorem~\ref{thm:resonance-filtered-bar-cobar} for the
decomposition $\cA = R_\cA \;\widehat{\oplus}\; \cA^{>0}$
with $R_\cA = V_0$ and $\cA^{>0} = \bigoplus_{h > 0} V_h$.

\emph{Hypothesis~(1):} the positive-weight sector $\cA^{>0}$
satisfies stabilized completion.  By Step~2, the transferred
operations on $\cA^{>0}$ decompose by weight shift.  In the
bar complex of $\cA^{>0}$, the differential either preserves
or strictly decreases total conformal weight of bar words
(each OPE residue decreases total weight by at least~$1$).
Therefore the bar complex at total weight~$w$ sees only
algebra elements of weight $\le w$; this is the stabilization
property of
Theorem~\ref{thm:stabilized-completion-positive} applied to
the \emph{total conformal weight of bar words} (which is
bounded and decreasing under the differential, ensuring
weightwise finiteness).

\emph{Hypothesis~(2):} $R_\cA = V_0$ is finite-dimensional
by Step~3, and it is a curved $A_\infty$-subalgebra because:
the curvature $m_0 \in V_0$ (it is the central-charge/vacuum
term), the higher operations $m_k|_{V_0^{\otimes k}} = 0$ for
$k \ge 2$ (since the OPE mode $v_{(n)}w$ for $v, w \in V_0$
has output weight $-n-1 < 0$, which vanishes by positive
energy), and $m_1|_{V_0} = 0$ (the transferred differential
preserves weight by Step~1, and is zero on the weight-$0$
cohomology).

\emph{Hypothesis~(3):} mixed operations with at least one
$\cA^{>0}$-input strictly raise positive weight \emph{in the
bar complex}.  This requires a sign clarification.  In the
completed tensor product
$\widehat{\bar B}^{\mathrm{res}}(\cA) =
\widehat{\bar B}^{\mathrm{st}}(\cA^{>0}) \;\widehat{\otimes}\;
\bar B(R_\cA)$,
the ``positive weight'' of a tensor element
$\alpha \otimes \beta$ is defined as the total conformal
weight of $\alpha \in \bar B(\cA^{>0})$.  The mixed
differential $D_{\mathrm{mix}}$ has two components:
(a)~interactions of $R_\cA$-elements with
$\cA^{>0}$-elements, and
(b)~$\cA^{>0}$-collisions whose outputs land in $R_\cA$.
For~(a): by the vacuum property, $v_{(n)}a = 0$ and
$a_{(n)}v = 0$ for all $v \in V_0$, $a \in \cA^{>0}$,
$n \ge 0$ (the vacuum annihilates under singular OPE, and the
only nonzero mode $a_{(-1)}|0\rangle = a$ is regular, hence
invisible to the bar differential which extracts only singular
residues).  For~(b): an $\cA^{>0}$-collision
$a_{(n)}b \in V_0$ requires $h(a) + h(b) - n - 1 = 0$,
i.e., the collision absorbs all positive weight into
$V_0$.  In the bar complex, this means a bar word
$[\cdots | a | b | \cdots]$ of positive weight~$w$ maps to a
bar word with positive weight $w - h(a) - h(b)$ and one
additional $R_\cA$-factor.  Since the total conformal weight
$w$ is finite and each such collapse strictly decreases
positive weight, the mixed differential is topologically
nilpotent: $D_{\mathrm{mix}}^n$ vanishes for $n$ exceeding
$\lfloor w / h_{\min} \rfloor$ where
$h_{\min} = \min\{h > 0 : V_h \ne 0\} \ge 1$.

\emph{Remark on directionality.}  The mixed differential
here is \emph{weight-decreasing} (positive weight flows from
$\cA^{>0}$ into $R_\cA$), not weight-increasing.  The
convergence argument is the same: topological nilpotence of
$D_{\mathrm{mix}}$ in the completed topology, since each
application decreases positive weight by a positive amount
bounded below by~$h_{\min}$.  The
filtered homological perturbation lemma applies with the
\emph{decreasing} positive-weight filtration
$\mathcal{F}^p = \{\text{bar chains with positive weight}
\le p\}$, which is preserved by~$D_{\mathrm{mix}}$.

\emph{Completion.}
With hypotheses~(1)--(3) verified (the third in the
topologically nilpotent sense just established),
Theorem~\ref{thm:resonance-filtered-bar-cobar} gives the
completed bar coalgebra decomposition and the cobar recovery.

The specific resonance ranks for the standard families are
computed in Proposition~\ref{prop:resonance-ranks-standard}:
$\rho = 0$ for quadratic and positive-tower families, and
$\rho = 1$ for Virasoro and $\mathcal{W}_N$
(the single resonance direction being the curvature $m_0$).
\end{proof}

\begin{remark}[The mode algebra vs.\ state-space formulation]
\label{rem:mode-vs-state-completion}
The proof crucially uses the \emph{state-space} formulation of the
chiral algebra (positive-energy grading on the VOA state space),
not the \emph{mode algebra} formulation (generators $L_n$ for
all~$n \in \mathbb{Z}$).  In the mode algebra, the coproduct
of~$L_0$ involves infinitely many terms
$L_k \otimes L_{-k}$, and the raw mode bar construction has
infinite-dimensional weight-$0$ part.  The positive-energy
state-space formulation avoids this: each weight space is
finite-dimensional by axiom, and the SDR is constructed weight by
weight.  The passage from modes to states is the HTT
(Theorem~\ref{thm:chiral-htt}), and the weight compatibility
(Step~2 above) ensures that the resonance piece remains
finite-dimensional after transfer.
\end{remark}

\begin{construction}[Completion towers as MC4 inverse limits]
\label{constr:completion-mc4}
The strong completion-tower theorem
(Theorem~\ref{thm:completed-bar-cobar-strong}) resolves MC4
by the arity cutoff lemma
(Lemma~\ref{lem:arity-cutoff}): the strong filtration axiom
\[
\mu_r(F^{i_1}, \ldots, F^{i_r})
\subset F^{i_1 + \cdots + i_r}
\]
ensures that continuity and Mittag-Leffler are automatic,
yielding the completed bar-cobar homotopy equivalence on
$\operatorname{CompCl}(\mathcal{F}_{\mathrm{ft}})$.  The
resonance rank $\rho(\cA)$
(Definition~\ref{def:resonance-rank}) classifies completion
difficulty.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{MC4$^+$ (positive towers, $\rho = 0$).}
  Weight stabilization
  (Theorem~\ref{thm:stabilized-completion-positive})
  reduces the completed bar-cobar problem to a finite
  verification at each weight: the transition maps
  $\widehat{\bar B}_{k+1}/F^{n+1}
  \twoheadrightarrow
  \widehat{\bar B}_k/F^n$
  stabilize for $n$ exceeding a bound depending only on
  the weight grading, so
  $\varprojlim^1 = 0$ and the inverse limit is exact.
  Examples: $\mathcal{W}_{1+\infty}$, affine Yangians,
  RTT algebras.
\item \emph{MC4$^0$ (resonant towers, $\rho > 0$).}
  The resonance-filtered bar-cobar
  (Theorem~\ref{thm:resonance-filtered-bar-cobar})
  decomposes the problem into a finite-dimensional
  resonance piece $R_\cA$ and a positive complement:
  $\widehat{\bar B}(\cA)
  \simeq
  \widehat{\bar B}^{\mathrm{st}}(\cA^+)
  \,\widehat{\otimes}\,
  \bar B(R_\cA)$.
  The completion difficulty is concentrated in the
  finite-dimensional factor $\bar B(R_\cA)$.
  Examples: $\mathrm{Vir}_c$ ($\rho = 1$),
  non-quadratic $\mathcal{W}_N$ ($\rho < \infty$,
  Theorem~\ref{thm:platonic-completion}).
\item The coefficient-stability criterion
  (Theorem~\ref{thm:coefficient-stability-criterion})
  reduces convergence of the completed bar-cobar to
  finite matrix stabilization at each weight window,
  and the uniform PBW bridge
  (Theorem~\ref{thm:uniform-pbw-bridge}) connects
  MC1 (PBW concentration) to MC4 (completed
  bar-cobar): every PBW-concentrated chiral algebra
  admits a completed bar-cobar homotopy equivalence.
\end{enumerate}
\end{construction}

\begin{remark}[MC4 execution programme]
\label{rem:mc4-execution-programme}
The correct execution order for the MC4 frontier, given the
splitting of Remark~\ref{rem:mc4-splitting}, is:
\begin{enumerate}
\item \emph{Promote Theorem~\textup{\ref{thm:stabilized-completion-positive}}
  to the main MC4 theorem.}
  Positive towers are declared reduced to weightwise stabilization.
  This shrinks MC4 to the resonant regime.
\item \emph{Solve the unshifted completed envelope first.}
  For Yangian/$\mathcal{W}_{1+\infty}$-type targets, prove
  completed bar-cobar for the unshifted completed envelope before
  touching shifted quotients.  The kernel
  $\to$ completed envelope $\to$ boundary quotient order is
  dictated by the coideal structure
  \textup{(}Appendix~\textup{\ref{chap:shifted-rtt-orthogonal-coideals}}\textup{)}.
\item \emph{Add quotient/coideal descent.}
  Prove that orthogonal coideals and shifted quotients descend
  through completion.  The shift is not the local problem; it is
  the boundary quotient problem.  BFN-type shifted data should
  appear at this stage.
\item \emph{Build the Virasoro resonance model.}
  Construct a positive-energy filtration on the Virasoro
  state-space bar complex, isolate the finite-dimensional
  resonance piece $R_{\mathrm{Vir}}$, and verify the hypotheses
  of Remark~\textup{\ref{rem:virasoro-resonance-model}}.
\item \emph{Only then return to MC5.}
  The dependency chain
  $\text{MC3} \Rightarrow \text{MC4} \Rightarrow \text{MC5}$
  remains inviolable (MC3 proved for all simple types; MC4 proved).  The BV/BRST physics dictionary
  becomes mathematically well-posed only after the completed
  bar-cobar machine is in place.
\end{enumerate}
\end{remark}

\section{Summary}

\begin{remark}[Completed frontier package]\label{rem:nilpotent-main}
This appendix should be read as a frontier package, not as a blanket
extension of the proved core.  What is currently in hand is:
\begin{enumerate}
\item the finite-stage convergence and geometry of the completed bar
      tower
      \textup{(}Theorem~\ref{thm:completion-convergence},
      Proposition~\ref{prop:geom-conilpotent}\textup{)};
\item the inverse-limit criteria used by the standard
      $\mathcal{W}_\infty$ and Yangian towers in the MC4 package of
      Chapter~\ref{chap:concordance};
\item the compatibility of these completed models with the
      Beilinson--Drinfeld filtered framework
      \textup{(}Theorem~\ref{thm:BD-chiral-homology}\textup{)};
\item the MC4 splitting into positive
  \textup{(}$\mathrm{MC4}^+$, resolved by stabilization\textup{)}
  and resonant \textup{(}$\mathrm{MC4}^0$\textup{)} regimes
  \textup{(}Remark~\ref{rem:mc4-splitting}\textup{)};
\item stabilized completion for positive towers
  \textup{(}Theorem~\ref{thm:stabilized-completion-positive}\textup{)};
\item the resonance rank invariant
  \textup{(}Definition~\ref{def:resonance-rank}\textup{)}
  and resonance-filtered completed bar-cobar
  \textup{(}Theorem~\ref{thm:resonance-filtered-bar-cobar}\textup{)};
\item the Platonic completion theorem
  \textup{(}Theorem~\ref{thm:platonic-completion}\textup{)},
  which proves that every positive-energy chiral algebra has
  finite resonance rank, identifying the irreducible core of MC4
  as a finite resonance problem.
\end{enumerate}
The Platonic completion theorem
\textup{(}Theorem~\ref{thm:platonic-completion}\textup{)}
is the sharp form of the MC4 content:
every positive-energy chiral algebra has finite resonance rank,
so ``MC4'' is a finite-dimensional problem sitting atop an
already-solved positive-weight stabilization machine.
What remains at the frontier is the \emph{Virasoro resonance
model}: the explicit computation of the resonance spectral
sequence for $\mathrm{Vir}_c$ and the non-quadratic
$\mathcal{W}_N$ algebras (Remark~\ref{rem:virasoro-resonance-model}),
and the identification of the H-level Koszul dual via
the higher pages of the spectral sequence.
\end{remark}
