\chapter[Ambient complementarity and nonlinear modular shadows]{Ambient complementarity, nonlinear modular shadows, and the quartic resonance class}
\label{app:nonlinear-modular-shadows}

The modular characteristic $\kappa(\cA)$ (Theorem~D) and the spectral
discriminant~$\Delta_{\cA}$ are the linear face of a single ambient
deformation problem.  The ambient problem carries a $(-1)$-shifted
symplectic form, and the two dual packages $\mathcal{Q}_g(\cA)$
and~$\mathcal{Q}_g(\cA^{!})$ are complementary Lagrangians inside it.
Their interaction produces an infinite nonlinear tower
\[
\kappa \;\longrightarrow\; \Delta \;\longrightarrow\;
\mathfrak{C} \;\longrightarrow\; \mathfrak{Q}
\;\longrightarrow\; \Theta,
\]
the \emph{shadow Postnikov tower}: the sequence of finite-order
projections $\Theta_\cA^{\leq r}$ of the universal MC element
$\Theta_\cA \in \MC(\gAmod)$
(Theorem~\ref{thm:mc2-bar-intrinsic}: $\Theta_\cA := D_\cA - d_0$
is MC because $D_\cA^2 = 0$; all-arity convergence
$\Theta_\cA = \varprojlim_r \Theta_\cA^{\leq r}$ by
Theorem~\ref{thm:recursive-existence}).

The construction proceeds in three strata.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Formal and conditional.}  The cyclic deformation package and the universal twisting kernel yield an ambient complementarity formal moduli problem, a complementarity potential~$S_\cA$, and a derived critical-locus model $\mathrm{Crit}(S_\cA)$ for simultaneous self-dual deformations.
\item \textbf{Finite-order and constructive.}  The quadratic, cubic, and quartic shadows
\[
H_{\cA},\qquad \mathfrak C_{\cA},\qquad \mathfrak Q_{\cA}
\]
are defined at each finite truncation~$\Theta_\cA^{\leq r}$, with master and clutching identities and a quartic shadow graph cocycle.
\item \textbf{Nonlinear and modular.}  For Virasoro and principal $\mathcal W_N$, the quartic contact sector has a determinant line whose vanishing promotes the Gram-determinant divisor to a modular characteristic class.  Its boundary law is the first nonlinear shadow of the clutching identity for~$\Theta_{\cA}$.
\end{enumerate}

\begin{remark}[Shadow tower as period correction]%
\label{rem:shadow-period-correction}%
\index{period correction!shadow tower}%
The shadow hierarchy $\kappa \to \Delta \to \mathfrak{C}
\to \mathfrak{Q} \to \Theta$ admits a concrete interpretation
as the Taylor expansion of the \emph{full period correction}
that restores nilpotency of the genus-$g$ bar differential.
At genus~$g$, the fiberwise differential satisfies
$d_{\mathrm{fib}}^2 = \kappa \cdot \omega_g \neq 0$.
The total corrected differential
$\Dg{g} = d_0 + \sum_{n \geq 1} t_g^{(n)} d_n$
absorbs this curvature:
\begin{itemize}
\item $t_g^{(1)}$: determined by $\kappa$ alone (the $m_2$
  contribution; Theorem~\ref{thm:modular-characteristic}).
  This is the Faber--Pandharipande term.
\item $t_g^{(2)}$: involves $m_3$ paired with genus-$g$
  propagators, giving the cubic shadow~$\mathfrak{C}_{\cA}$.
\item $t_g^{(3)}$: involves $m_4$ and $m_3 \circ m_3$ terms,
  giving the quartic shadow~$\mathfrak{Q}_{\cA}$.
\item $t_g^{(\infty)}$: the all-arity limit is
  $\Theta_{\cA}$, the universal Maurer--Cartan element
  (Theorem~\ref{thm:mc2-bar-intrinsic}).
\end{itemize}
The subleading corrections $t_g^{(n)}$ for $n \geq 2$ are
\emph{not} determined by~$\kappa$: they depend on the
higher $A_\infty$ operations interacting with the Hodge data of
$\overline{\mathcal{M}}_g$.  This is the mechanism by which
algebra-dependent modular information enters beyond the
$\hat{A}$-genus.  The cohomology
$H^*(\barB^{(g)}(\cA), \Dg{g})$ (the factorization homology
fiber) depends on the \emph{full} correction, not just the
leading term.  See Remark~\ref{rem:four-levels}.
\end{remark}

\medskip
\noindent\emph{Status discipline.}
The universal Maurer--Cartan class $\Theta_\cA$ exists unconditionally for every modular Koszul chiral algebra, by the bar-intrinsic construction (Theorem~\ref{thm:mc2-bar-intrinsic}): one sets $\Theta_\cA := D_\cA - \dzero$, where $D_\cA$ is the genus-completed bar differential, and the Maurer--Cartan equation is the tautological consequence of $D_\cA^2 = 0$.  The shadow Postnikov tower $\Theta_\cA^{\leq r}$ consists of the finite-order projections of this proved element.  The \emph{constructive} value of the tower is computational: each level yields explicit graph-sum formulas (vertex labels from the transferred cyclic minimal model, edge contractions by the complementarity propagator) that the bar-intrinsic construction does not directly produce.  The obstruction classes $o_{r+1}(\cA) \in H^2(\cA^{\mathrm{sh}}_{r+1,0})$ measure the failure of \emph{truncation} (can the arity-$r$ approximation be extended one step further without changing its lower-order terms?), not the failure of \emph{existence}.  Every theorem below is tagged either as proved here, as a formal consequence of the bar-intrinsic construction, or as conjectural at the level of the \emph{Hamiltonian refinement} (the graph-completed modular master action of \S\ref{sec:nms-feynman-transform-programme}).

\begin{remark}[Prefundamental CG and the shadow tower]
\label{rem:nms-prefundamental-cg}
\index{shadow tower!prefundamental compatibility}
The finite-order constructive layer (shadows $H_\cA$, $C_\cA$,
$Q_\cA$ at arities~$2$, $3$, $4$) interacts with the MC3
prefundamental programme as follows.  By the prefundamental
Clebsch--Gordan ($V_n \otimes L^- \cong \bigoplus L^-(\text{shifted})$,
Theorem~\ref{thm:shifted-prefundamental-generation}), the
evaluation-stable part of the Yangian category is preserved by the
$V_n$-twist that generates the shadow tower's clutching maps
$\Lambda_P \colon \operatorname{Sym}^r \to \operatorname{Sym}^{r-2}$.
This means that the tower of shadow obstructions
$\{o^{(r)}_\cA\}_{r \geq 3}$, governed by the master equation
$\nabla_H(\mathrm{Sh}_r) + o^{(r)} = 0$
(Theorem~\ref{thm:nms-all-arity-master-equation}),
restricts naturally to the prefundamental evaluation-stable sector.
In particular, the quartic contact invariant $Q^{\mathrm{contact}}$
and the finite termination results for Heisenberg ($r = 2$),
affine ($r = 3$), and $\beta\gamma$ ($r = 4$) are all compatible
with the $K_0$ tensor structure determined by~(R1).
\end{remark}

%% ----------------------------------------------------------------
%% GOD-CANONICAL: The universal Maurer--Cartan principle
%% ----------------------------------------------------------------

\providecommand{\gAmod}{\mathfrak{g}_{\cA}^{\mathrm{mod}}}

\section{The universal Maurer--Cartan principle}
\label{sec:nms-universal-mc-principle}

The thesis of this monograph is that the modular data of a chiral algebra (the genus
corrections, the shadow tower, the non-renormalization theorems, the clutching
identities) are not independent structures assembled by hand.  They are all
consequences of a \emph{single} Maurer--Cartan equation in a \emph{single} dg~Lie
algebra.  This section states the organizing principle.  The rest of the chapter
develops its explicit consequences.

\begin{definition}[Modular convolution dg~Lie algebra; \ClaimStatusProvedHere]
\label{def:nms-modular-convolution-lie}%
\index{modular convolution dg Lie algebra}%
\index{g_A^mod@$\gAmod$|see{modular convolution dg Lie algebra}}%
Let $\cA$ be a chiral algebra on a smooth projective curve with Koszul
dual~$\cA^!$ on the locus where the duality package is defined.
The following completed dg~Lie algebra is the \emph{strict model}
of the modular quantum $L_\infty$-algebra
(Remark~\ref{rem:nms-linfty-enrichment}); its Maurer--Cartan moduli
coincide with those of the full $L_\infty$-algebra.
The \emph{modular convolution dg~Lie algebra} is the completed product
\[
  \gAmod
  \;:=\;
  \prod_{\substack{g,n \geq 0 \\ 2g-2+n>0}}
  \operatorname{Hom}_{S_n}\!\bigl(
    C_\bullet(\overline{\mathcal{M}}_{g,n+1}),\;
    \operatorname{Hom}\bigl((\cA^{!})^{\otimes n},\, \cA^{!}\bigr)
  \bigr),
\]
graded by genus~$g$ (homological weight) and arity~$n$, with
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Differential}
  $d_{\partial}\colon \gAmod \to \gAmod$
  induced by the boundary stratification
  $\partial\overline{\mathcal{M}}_{g,n} \hookrightarrow
  \overline{\mathcal{M}}_{g,n}$, i.e.\ by pullback along the
  clutching morphisms of the Deligne--Mumford modular operad;
\item \textbf{Bracket}
  $[\,\cdot\,,\,\cdot\,]\colon
  \gAmod \otimes \gAmod \to \gAmod$
  given by operadic composition via stable-graph gluing:
  for $f$ in the $(g_1,n_1)$-component and
  $g$ in the $(g_2,n_2)$-component of~$\gAmod$, the bracket
  $[f,g]_{g,n}$ is the signed sum over all stable graphs of
  genus~$g = g_1 + g_2$ (or $g = g_1 + g_2 + 1$ for
  self-gluing) obtained by inserting the output of~$g$
  into an input of~$f$ and composing with the
  Deligne--Mumford clutching map.
\end{enumerate}
The Jacobi identity follows from the associativity of operadic composition, and $d_\partial^2=0$ from the cosimplicial identities of the modular operad's boundary strata.
By Theorem~\ref{thm:operadic-homotopy-convolution}, $\gAmod$ is the
chiral instance of the convolution $s\mathscr{L}_\infty$-algebra
$\operatorname{hom}^\alpha(D,A)$ of Robert-Nicoud--Wierstra~\cite{RNW19},
with $\alpha = \tau_{\mathrm{ch}}$ the chiral twisting morphism.
\end{definition}

\begin{remark}[The modular $L_\infty$ enrichment]
\label{rem:nms-linfty-enrichment}
The modular convolution algebra $\gAmod$ carries a natural modular
$L_\infty$ structure whose higher brackets $\ell_k$ ($k \geq 3$)
arise from the Feynman transform of the modular operad
$\{C_\bullet(\overline{\cM}_{g,n})\}$ via $A_\infty$/$L_\infty$
homotopy transfer \cite[\S10.3]{LV12}.  The dg~Lie bracket $[-,-]$
is the binary truncation.  The Maurer--Cartan equation
\eqref{eq:nms-mc-equation} is the strict shadow of the full $L_\infty$
MC equation $\sum_{n \geq 1} \frac{1}{n!}\ell_n(\Theta,\ldots,\Theta) = 0$;
for the coderivation model these coincide (this is
the MC moduli identification invoked in
Definition~\ref{def:nms-modular-convolution-lie}).
The full $L_\infty$ MC equation admits \emph{gauge equivalences} (homotopies between MC elements):
two MC elements related by $L_\infty$ gauge transform give
quasi-isomorphic bar complexes.  This is the homotopy-theoretic reason
that bar-cobar inversion (Theorem~B) is well-defined up to
quasi-isomorphism.
\end{remark}

\begin{theorem}[Algebra structure $=$ Maurer--Cartan element; \ClaimStatusProvedHere]
\label{thm:nms-mc-principle}%
\index{Maurer--Cartan element!modular}%
\index{Theta_A@$\Theta_{\cA}$!as Maurer--Cartan element}%
An algebra structure on~$\cA$ together with its genus-refined modular data
is equivalent to a Maurer--Cartan element
$\Theta_{\cA} \in \mathrm{MC}(\gAmod)$ satisfying
\begin{equation}\label{eq:nms-mc-equation}
  d_\partial\,\Theta_{\cA}
  \;+\;
  \tfrac{1}{2}\bigl[\Theta_{\cA},\,\Theta_{\cA}\bigr]
  \;=\; 0.
\end{equation}
Explicitly: the genus-$g$, arity-$n$ component of~$\Theta_{\cA}$ is
the multilinear operation $(\cA^{!})^{\otimes n} \to \cA^{!}$
obtained by evaluating the $A_\infty$ operations and their modular
corrections against the fundamental chain
$[{}\overline{\mathcal{M}}_{g,n+1}]$.
\end{theorem}

\begin{proof}[Proof sketch]
This is the modular-operad enhancement of the classical fact that an
$A_\infty$-structure is a codifferential on the bar construction (hence
a Maurer--Cartan element in the convolution Lie algebra
$\operatorname{Hom}(T^c(\cA^{!}[1]),\cA^{!})$).  The extension to
all genera uses the Deligne--Mumford modular operad structure on
$\{\overline{\mathcal{M}}_{g,n}\}$: the codifferential condition
$D^2=0$ on the modular bar complex is equivalent to the
Maurer--Cartan equation~\eqref{eq:nms-mc-equation} in~$\gAmod$.
The signs are fixed by the Koszul rule and the orientation conventions
of Appendix~\ref{app:signs}.
\end{proof}

\begin{proposition}[Shadow tower as $L_\infty$ formality obstruction tower; \ClaimStatusProvedHere]
\label{prop:shadow-linfty-obstruction}%
\index{shadow Postnikov tower!$L_\infty$ formality obstruction}%
\index{L-infinity formality@$L_\infty$ formality!shadow tower identification}%
The shadow Postnikov tower
$\Theta_{\cA}^{\leq 2} \to \Theta_{\cA}^{\leq 3}
\to \Theta_{\cA}^{\leq 4} \to \cdots$
coincides with the $L_\infty$ formality obstruction tower of the
modular convolution algebra~$\gAmod$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item At arity~$2$: the scalar shadow
  $\kappa(\cA) = \pi_{\mathrm{sc}}(\Theta_{\cA}^{\leq 2})$
  is the binary $L_\infty$-bracket $\ell_2^{(0)}$, which equals the
  classical Lie bracket of~$\gAmod$.
\item At arity~$3$: the cubic shadow $[\mathfrak{C}_{\cA}]$ is
  the transferred $L_\infty$-bracket $\ell_3^{(0),\mathrm{tr}}$,
  which is gauge-trivial when
  $H^1(F^3\mathfrak{g}/F^4\mathfrak{g}, d_2) = 0$
  (Theorem~\ref{thm:cubic-gauge-triviality}).
\item At arity~$4$: the quartic resonance class
  $[R^{\mathrm{mod}}_4(\cA)]$ is the first genuine $L_\infty$
  obstruction~$\ell_4^{(0),\mathrm{tr}}$
  after gauge trivialization of the cubic.
\item The shadow depth $r_{\max}(\cA)$ equals both the
  $A_\infty$-depth $d_\infty(\cA)$ and the
  $L_\infty$-formality level $f_\infty(\cA)$
  (Theorem~\ref{thm:operadic-complexity}).
\end{enumerate}
\end{proposition}

\begin{proof}
The arity filtration $F^r\gAmod$ on the modular convolution
algebra induces a Postnikov tower on the space of MC elements.
The shadow $\Theta_{\cA}^{\leq r}$ is by definition the
projection of the bar-intrinsic MC element
$\Theta_{\cA} := D_{\cA} - d_0$
(Theorem~\ref{thm:nms-mc-principle}) to $F^{\leq r}\gAmod$.

At arity~$2$, the MC equation reduces to the Jacobi identity
for $\ell_2^{(0)}$; its scalar trace is~$\kappa(\cA)$.
At arity~$3$, the obstruction to lifting
$\Theta_{\cA}^{\leq 2}$ to $\Theta_{\cA}^{\leq 3}$
lives in $H^2(F^3\gAmod/F^4\gAmod, d_2)$,
which is the same cohomology group controlling the
transferred $L_\infty$-bracket $\ell_3^{(0),\mathrm{tr}}$.
The gauge triviality theorem
(Theorem~\ref{thm:cubic-gauge-triviality}) identifies
the vanishing of~$H^1$ in the same graded piece as the
condition for removability.

At arity~$4$, after gauge-trivializing the cubic term, the
residual obstruction class in
$H^2(F^4\gAmod/F^5\gAmod, d_2)$
is the canonical quartic~$[R^{\mathrm{mod}}_4(\cA)]$.
This is exactly the transferred bracket
$\ell_4^{(0),\mathrm{tr}}$ of the homotopy transfer
from $(V_{\cA}, d_2, \ell_2^{(0)})$ to its cohomology, the
standard formula for the first non-trivial $L_\infty$ massey
product after a formal bracket.

These three identifications are proved
at arities $2$, $3$, $4$ by
Proposition~\ref{prop:shadow-formality-low-arity},
which establishes the coincidence of the shadow tower with
the $L_\infty$ formality obstruction tower at each arity
by direct comparison of the graph-sum formulae with the
homotopy transfer formulae.  The equality
$r_{\max} = d_\infty = f_\infty$ extends this to all arities
by Theorem~\ref{thm:operadic-complexity}.
\end{proof}

\begin{remark}[Termination as the new content]
\label{rem:shadow-termination-novelty}
\index{shadow Postnikov tower!termination}
The identification of the shadow tower with the
$L_\infty$ formality obstruction tower is structural:
the homological perturbation lemma (HPL) produces a
transferred $L_\infty$-algebra on any retract, and the
transferred brackets $\ell_r^{\mathrm{tr}}$ always exist.
The genuinely new content of
Proposition~\ref{prop:shadow-linfty-obstruction} is the
\emph{termination} phenomenon: the transferred $L_\infty$-algebra
terminates at arity $r_{\max}(\cA)$, meaning
$\ell_r^{\mathrm{tr}} = 0$ for all $r > r_{\max}$.  This
is a consequence of the shadow tower analysis
(Theorem~\ref{thm:shadow-archetype-classification}),
not the HPL itself.  The HPL is agnostic about termination;
it produces infinitely many brackets in general.  What
forces termination is the specific structure of the modular
convolution algebra: the vanishing of obstruction classes
$o^{(r+1)}(\cA)$ in
$H^2(F^{r+1}\gAmod/F^{r+2}\gAmod, d_2)$
for $r > r_{\max}$, which reflects the OPE complexity of~$\cA$.
\end{remark}

\begin{proposition}[Five-component decomposition; \ClaimStatusProvedHere]
\label{prop:nms-five-component}%
\index{five-component decomposition}%
Expanding $\Theta_{\cA}$ by genus and boundary type yields
\[
  \Theta_{\cA}
  \;=\;
  \Theta^{\mathrm{tree}}
  + \Theta^{\mathrm{sew}}
  + \hbar\,\Theta^{\mathrm{loop}}
  + \Theta^{r}
  + \Theta^{\mathrm{bdry}},
\]
and the Maurer--Cartan equation~\eqref{eq:nms-mc-equation} decomposes
into five interlocking pieces:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item \textbf{Genus~$0$, tree-level:}
  the $d_{A_\infty}$ piece: the transferred $A_\infty$ operations
  $\{m_n\}_{n \geq 2}$;
\item \textbf{Genus~$0$, self-gluing:}
  the $d_{\mathrm{sew}}$ piece: self-gluing of genus-$0$ operations
  (the cyclic $A_\infty$ constraint);
\item \textbf{Genus~$g \geq 1$, non-separating:}
  the $\hbar\,\Delta$ piece: BV contraction, the genus-raising
  operator;
\item \textbf{Spectral:}
  the $d_r$ piece: the line-operator twist by~$r(z)$;
\item \textbf{Boundary strata:}
  the $d_{\mathrm{bdry}}$ piece: clutching maps along
  $\partial\overline{\mathcal{M}}_{g,n}$.
\end{enumerate}
In particular, the total differential
$D = d_{A_\infty} + d_{\mathrm{sew}} + \hbar\,\Delta + d_r$
is \emph{not} five independent structures assembled by fiat.  It is
the single equation~\eqref{eq:nms-mc-equation} expanded by stratum.

In the three-pillar framework
(\S\ref{sec:concordance-three-pillars}): pieces~(1)--(2) carry the
Pillar~B convolution $sL_\infty$ structure
(Theorem~\ref{thm:operadic-homotopy-convolution}); piece~(3) is the
BV operator from the modular operad boundary; pieces~(4)--(5) encode
the Pillar~C log-FM collision geometry, with the planted-forest
differential $d_{\mathrm{pf}}$ arising as the tropical skeleton of
$\overline{\operatorname{FM}}_n(C|D)$
(Theorem~\ref{thm:planted-forest-tropicalization}).  Pillar~A (the
Ch$_\infty$ structure) governs the $L_\infty$ coherence that makes
$D^2 = 0$ hold despite these five terms interacting nontrivially.
\end{proposition}

\begin{proof}
Stratify $\gAmod$ by genus and partition the boundary strata of
$\overline{\mathcal{M}}_{g,n}$ into separating, non-separating, and
tree-level.  The Maurer--Cartan equation is additive in genus and
boundary type; projecting onto each stratum yields the five terms.
The BV operator~$\Delta$ arises from the non-separating node
stratum $\delta_{\mathrm{irr}} \colon
\overline{\mathcal{M}}_{g-1,n+2} \to
\overline{\mathcal{M}}_{g,n}$, which raises genus by~$1$.
\end{proof}

\begin{theorem}[Shadow tower from MC evaluation; \ClaimStatusProvedHere]
\label{thm:nms-shadow-tower-mc}%
\index{shadow tower!from Maurer--Cartan evaluation}%
The shadow hierarchy
$\kappa \to \Delta \to \mathfrak{C} \to \mathfrak{Q} \to \Theta$
is the evaluation of~$\Theta_{\cA}$ on specific moduli classes:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\kappa(\cA) =
  \langle \Theta_{\cA},\, \Theta_{\cA} \rangle$
  paired with
  $[\overline{\mathcal{M}}_{1,1}]$
  (the fundamental class of genus-$1$ moduli);
\item $\Delta_{\cA} =$
  spectral data of~$\Theta_{\cA}\big|_{\overline{\mathcal{M}}_{1,2}}$
  (restriction to $2$-pointed genus~$1$);
\item $\mathfrak{C}_{\cA} =
  \Theta_{\cA}\big|_{\overline{\mathcal{M}}_{0,4}}$
  (quartic genus-$0$ boundary stratum);
\item $\mathfrak{Q}_{\cA} =$
  the contact term of~$\Theta_{\cA}$ on
  $\overline{\mathcal{M}}_{0,5}$
  (quintic boundary);
\item the full $\Theta_{\cA}$ \emph{is} the universal
  Maurer--Cartan element itself.
\end{enumerate}
\end{theorem}

\begin{proof}
Each shadow is by definition the value of the genus-refined
multilinear data on an explicit cycle representative in
$H_*(\overline{\mathcal{M}}_{g,n})$.
Item~(i) is Theorem~D specialized to genus~$1$; items~(ii)--(iv)
are the definitions of
$\Delta_{\cA}$, $\mathfrak{C}_{\cA}$, $\mathfrak{Q}_{\cA}$
from Section~\ref{sec:nms-shadow-calculus}.  The hierarchy
$\kappa \to \Delta \to \mathfrak{C} \to \mathfrak{Q} \to \Theta$
is the filtration of~$\gAmod$ by arity: each shadow is the
next Taylor coefficient of the single element~$\Theta_{\cA}$.
\end{proof}

\begin{corollary}[All families from universal evaluation; \ClaimStatusProvedHere]
\label{cor:nms-all-families-universal}%
\index{shadow tower!family evaluation}%
For each standard family (Heisenberg, affine Kac--Moody,
Virasoro, $\mathcal{W}_3$, Yangian), the specific formulas
($\kappa$~values, shadow tower data, genus corrections) computed
in Part~II are obtained by evaluating~$\Theta_{\cA}$ on
explicit cycle representatives in
$H_*(\overline{\mathcal{M}}_{g,n})$.
No additional input is needed beyond the algebra structure
and the moduli geometry.
\end{corollary}

\begin{remark}[The Chriss--Ginzburg principle]
\label{rem:nms-chriss-ginzburg}%
\index{Chriss--Ginzburg principle}%
This is the ``one object, one equation, everything else is a
corollary'' paradigm.  The modular convolution dg~Lie
algebra~$\gAmod$ is the single organizing structure.  The quantum
master equation, the graph sums, the genus tower, the
non-renormalization theorems, the shadow projections: all are
automatic from $\Theta_{\cA} \in \mathrm{MC}(\gAmod)$.
The rest of this chapter develops the explicit consequences.
\end{remark}

\section{The governing question from first principles}
\label{sec:nms-governing-question}

The correct theorem of complementarity is not
\[
Q_g(\cA)\oplus Q_g(\cA^!) \cong C_g(\cA).
\]
That is only the linear shadow.  The correct theorem is that there is a single formal moduli problem carrying a shifted symplectic structure, and the two dual deformation packages are Lagrangian inside it.  The first-principles data are therefore not two vector spaces and a bookkeeping identity, but:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item a cyclic deformation complex for $\cA$,
\item a cyclic deformation complex for $\cA^!$,
\item a universal twisting kernel relating the two,
\item a cyclic pairing turning the total deformation problem into a shifted symplectic formal moduli problem.
\end{enumerate}

This is exactly the geometric shape suggested by the chiral bar--cobar formalism.  The bar--cobar kernel is not auxiliary bookkeeping; it is the object whose deformations simultaneously remember the deformation of $\cA$, the deformation of $\cA^!$, and the compatibility between them.

\section{Ambient complementarity from first principles}
\label{sec:nms-ambient-complementarity}

\begin{definition}[Ambient complementarity datum]
\label{def:nms-ambient-datum}
Let $\cA$ be a modular Koszul chiral algebra on a smooth projective curve, and let $\cA^!$ denote its Koszul dual on the locus where the duality package is defined.  An \emph{ambient complementarity datum} consists of:
\begin{enumerate}[label=\textup{(\roman*)}]
\item two cyclic deformation complexes
\[
L_{\cA}:=\Defcyc(\cA),\qquad L_{\cA^!}:=\Defcyc(\cA^!),
\]
viewed as filtered complete cyclic $L_\infty$-algebras;
\item a completed kernel object
\[
K_{\cA}:=(\cA^!\widehat\otimes \cA)[1]
\]
with differential twisted by the universal twisting kernel;
\item a Maurer--Cartan element
\[
\tau_{\cA}\in \mathrm{MC}(\cA^!\widehat\otimes \cA)
\]
representing the canonical bar--cobar twisting kernel;
\item linearizations of the kernel in the two deformation directions,
\[
\nabla_{\cA}:L_{\cA}\to K_{\cA},
\qquad
\nabla_{\cA^!}:L_{\cA^!}\to K_{\cA};
\]
\item a degree $-1$ cyclic pairing on the total complex
\[
L_{\cA}\oplus K_{\cA}\oplus L_{\cA^!}
\]
for which the kernel differential is skew-adjoint.
\end{enumerate}
\end{definition}

\begin{definition}[Ambient complementarity tangent complex]
\label{def:nms-ambient-tangent-complex}
Given an ambient complementarity datum, define the \emph{ambient complementarity tangent complex}
\begin{equation}
\label{eq:nms-ambient-tangent}
T_{\mathrm{comp}}(\cA)
:=
\mathrm{fib}\Bigl(
\nabla_{\cA}-\nabla_{\cA^!}:
L_{\cA}\oplus L_{\cA^!}\longrightarrow K_{\cA}
\Bigr).
\end{equation}
A tangent vector in $T_{\mathrm{comp}}(\cA)$ is therefore a first-order deformation of $\cA$, a first-order deformation of $\cA^!$, and a first-order deformation of the universal kernel, constrained by the linearized Maurer--Cartan equation.
\end{definition}

\begin{theorem}[Ambient complementarity in tangent form; \ClaimStatusProvedHere]
\label{thm:nms-ambient-complementarity-tangent}
Assume an ambient complementarity datum exists for $\cA$.  Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the complex $T_{\mathrm{comp}}(\cA)$ carries a canonical nondegenerate pairing of degree $-1$;
\item the one-sided tangent complexes
\[
T_{\cA}:=\mathrm{fib}(\nabla_{\cA}:L_{\cA}\to K_{\cA}),
\qquad
T_{\cA^!}:=\mathrm{fib}(\nabla_{\cA^!}:L_{\cA^!}\to K_{\cA})
\]
are isotropic inside $T_{\mathrm{comp}}(\cA)$;
\item if the pairing on $L_{\cA}\oplus K_{\cA}\oplus L_{\cA^!}$ is perfect and bar--cobar duality identifies the normal complex of one side with the shifted dual tangent complex of the other, then $T_{\cA}$ and $T_{\cA^!}$ are complementary Lagrangians in $T_{\mathrm{comp}}(\cA)$.
\end{enumerate}
\end{theorem}

\begin{proof}
The degree $-1$ pairing on $T_{\mathrm{comp}}(\cA)$ is induced from the cyclic pairing on the direct sum by passage to the homotopy fiber.  Because the total differential is skew-adjoint, the pairing descends to cohomology and is compatible with the differential.

For the one-sided tangent complex $T_{\cA}$, the pullback of the ambient pairing reduces to the quadratic term in the differentiated Maurer--Cartan equation for the universal kernel.  That quadratic term vanishes because the Maurer--Cartan equation is exactly the isotropy condition for the graph of the one-sided variation.  The same argument applies to $T_{\cA^!}$.

If the cyclic pairing is perfect and bar--cobar duality identifies the normal complex to one side with the shifted dual tangent complex of the other, maximal isotropicity follows.  This is precisely the derived form of the slogan that the two sides are opposite polarizations of a single symplectic deformation problem.\qedhere
\end{proof}

\begin{theorem}[Ambient complementarity as a shifted symplectic formal moduli problem; \ClaimStatusProvedElsewhere{} {\normalfont (see Theorem~\ref{thm:ambient-complementarity-fmp})}]
\label{thm:nms-ambient-complementarity-fmp}
Assume the tangent complex $T_{\mathrm{comp}}(\cA)$ integrates to a filtered complete cyclic $L_\infty$-algebra presenting a formal moduli problem
\[
\mathcal M_{\mathrm{comp}}(\cA).
\]
Then $\mathcal M_{\mathrm{comp}}(\cA)$ carries a canonical $(-1)$-shifted symplectic structure, and the one-sided deformation problems of $\cA$ and of $\cA^!$ define Lagrangian maps
\[
\mathcal M_{\cA}\longrightarrow \mathcal M_{\mathrm{comp}}(\cA)
\longleftarrow \mathcal M_{\cA^!}.
\]
The genus-$g$ complementarity complex is the linear shadow of this picture.
\end{theorem}

\begin{remark}[Why the theorem is stronger than additive complementarity]
\label{rem:nms-stronger-than-additive}
An additive splitting can always be faked by eigenspace decompositions, arbitrary direct sums, or linear bookkeeping identities.  The ambient theorem is harder to fake because it requires:
\begin{enumerate}[label=\textup{(\roman*)}]
\item a single deformation problem rather than two unrelated ones,
\item a shifted symplectic pairing on that problem,
\item isotropicity of the one-sided packages,
\item maximality of the isotropicity,
\item compatibility with clutching, factorization, and duality.
\end{enumerate}
The last item is decisive: the theorem is not only about tangent complexes at one point, but about a modular geometry stable under the basic operations of the theory.
\end{remark}

\subsection{Cotangent normal form and the complementarity potential}
\label{subsec:nms-cotangent-normal-form}

\begin{theorem}[Shifted cotangent normal form; \ClaimStatusProvedHere]
\label{thm:nms-cotangent-normal-form}
Let $\mathcal M$ be a pointed $(-1)$-shifted symplectic formal moduli problem, and let
\[
i_+\colon \mathcal L_+\to \mathcal M,
\qquad
 i_-\colon \mathcal L_-\to \mathcal M
\]
be pointed Lagrangian maps through the base point.  Assume the induced tangent map
\[
T_0\mathcal L_+\oplus T_0\mathcal L_- \xrightarrow{\sim} T_0\mathcal M
\]
is a quasi-isomorphism.  Then there exists a pointed formal symplectomorphism
\[
(\mathcal M,i_+)\simeq (T^*[-1]\mathcal L_+,0\text{-section})
\]
under which $\mathcal L_-$ becomes the graph of a closed degree-zero one-form
\[
\alpha_+\in \Omega^1(\mathcal L_+)^0.
\]
In the pointed formal neighborhood this one-form is exact:
\[
\alpha_+=dS_+
\]
for a degree-zero formal function $S_+$, unique up to an additive constant.
\end{theorem}

\begin{proof}
Because $i_+$ is Lagrangian, the normal complex of $\mathcal L_+$ in $\mathcal M$ is canonically identified with $T^*[-1]\mathcal L_+$.  Formally along $\mathcal L_+$, the symplectic neighborhood theorem gives a pointed equivalence with the shifted cotangent bundle.  Under this identification, $\mathcal L_+$ becomes the zero section.  Since $\mathcal L_-$ is complementary to the zero section, it is the graph of a one-form $\alpha_+$.  The graph of a one-form in a cotangent bundle is Lagrangian if and only if the one-form is closed, because the pullback of the canonical symplectic form is exactly $d\alpha_+$.  In a pointed formal neighborhood every closed one-form is exact, which produces $S_+$.\qedhere
\end{proof}

\begin{definition}[Complementarity potential]
\label{def:nms-complementarity-potential}
Assume the ambient complementarity formal moduli problem exists.  The formal function
\[
S_{\cA}\in \widehat{\mathcal O}(\mathcal M_{\cA})^0
\]
produced by Theorem~\ref{thm:nms-cotangent-normal-form} for the pair
\[
\mathcal L_+=\mathcal M_{\cA},
\qquad
\mathcal L_- = \mathcal M_{\cA^!}
\]
is called the \emph{complementarity potential} of the Koszul pair $(\cA,\cA^!)$.
\end{definition}

\begin{proposition}[Legendre duality of the two potentials; \ClaimStatusProvedHere]
\label{prop:nms-legendre-duality}
Assume the ambient complementarity formal moduli problem exists.  Let $S_{\cA}$ and $S_{\cA^!}$ be the complementarity potentials constructed from the two cotangent charts centered at $\mathcal M_{\cA}$ and $\mathcal M_{\cA^!}$.  Then $S_{\cA}$ and $S_{\cA^!}$ are formal Legendre transforms of one another.
\end{proposition}

\begin{proof}
The two functions generate the same formal Lagrangian subspace of the same shifted symplectic ambient moduli problem, viewed from the two opposite cotangent charts.  The coordinate change between these two charts is the formal Legendre transform.\qedhere
\end{proof}

\begin{proposition}[Legendre duality of cubic tensors; \ClaimStatusProvedHere]
\label{prop:nms-legendre-cubic}
Let $H_{\cA}$ be the complementarity Hessian.  Then the cubic shadows of $\cA$ and $\cA^!$ are related by formal Legendre duality:
\[
\mathfrak C_{\cA^!}(p,p,p)
= -\mathfrak C_{\cA}(H_{\cA}^{-1}p, H_{\cA}^{-1}p, H_{\cA}^{-1}p).
\]
More generally, at quartic order the Legendre transform gives
\[
S_{\cA}^\vee(p)
= \tfrac12 H_{\cA}^{-1}(p,p)
- \tfrac{1}{6}\mathfrak C_{\cA}(H_{\cA}^{-1}p,H_{\cA}^{-1}p,H_{\cA}^{-1}p)
+ O(p^4).
\]
Since $S_{\cA}^\vee = S_{\cA^!}$, the cubic shadow on the dual side is the Hessian-transported negative of the cubic shadow on the primal side.
\end{proposition}

\begin{proof}
Write $S_{\cA}(x) = \frac12 H_{\cA}(x,x) + \frac16 \mathfrak C_{\cA}(x,x,x) + O(x^4)$.  The critical point of $\langle p,x\rangle - S_{\cA}(x)$ is $x = H_{\cA}^{-1}p + O(p^2)$.  Substituting into the Legendre formula and collecting through cubic order yields the displayed identity.\qedhere
\end{proof}

\begin{theorem}[Derived critical locus of self-dual deformations; \ClaimStatusProvedHere]
\label{thm:nms-derived-critical-locus}
Assume the ambient complementarity formal moduli problem exists.  Then there is a canonical equivalence
\[
\mathcal M_{\cA}\times^h_{\mathcal M_{\mathrm{comp}}(\cA)}\mathcal M_{\cA^!}
\simeq
\mathrm{Crit}(S_{\cA}).
\]
Simultaneous deformations of $\cA$ and $\cA^!$ preserving complementarity are governed by the derived critical locus of the complementarity potential.
\end{theorem}

\begin{proof}
In the cotangent normal form of Theorem~\ref{thm:nms-cotangent-normal-form}, one Lagrangian is the zero section and the other is the graph of $dS_{\cA}$.  Their derived intersection is by definition the derived zero locus of $dS_{\cA}$, which is the derived critical locus of $S_{\cA}$.\qedhere
\end{proof}

\begin{proposition}[Criterion for fake complementarity; \ClaimStatusProvedHere]
\label{prop:nms-fake-complementarity}
In the cotangent chart centered at $\mathcal M_{\cA}$, the following are equivalent.
\begin{enumerate}[label=\textup{(\roman*)}]
\item The dual Lagrangian $\mathcal M_{\cA^!}$ is linear.
\item The complementarity potential $S_{\cA}$ is quadratic.
\item The derived critical locus $\mathrm{Crit}(S_{\cA})$ is controlled entirely by its Hessian complex, with no higher nonlinear operations.
\end{enumerate}
Consequently, the first obstruction to fake complementarity is the first nonzero higher jet of $S_{\cA}$ beyond its quadratic part.
\end{proposition}

\begin{proof}
In the cotangent chart, $\mathcal M_{\cA^!}$ is the graph of $dS_{\cA}$.  The graph is linear if and only if $dS_{\cA}$ is linear, hence if and only if $S_{\cA}$ is quadratic.  When $S_{\cA}$ is quadratic, its critical locus is cut out by a linear differential and is therefore governed by the Hessian complex alone.  Conversely, any cubic or higher term in $S_{\cA}$ produces a nonlinear contribution to $dS_{\cA}$ and therefore to the critical locus.\qedhere
\end{proof}

\section{Finite-order nonlinear shadow calculus}
\label{sec:nms-shadow-calculus}

The full universal class $\Theta_{\cA}$ globalizes the entire modular deformation theory (Theorem~\ref{thm:mc2-bar-intrinsic}).  Its first visible jets are accessible before the full globalization.

\begin{definition}[Arity shadows of the universal class]
\label{def:nms-arity-shadows}
By the bar-intrinsic construction (Theorem~\ref{thm:mc2-bar-intrinsic}), the universal Maurer--Cartan class
\[
\Theta_{\cA}\in \mathrm{MC}\bigl(\Defcyc(\cA)\widehat\otimes \mathbb G_{\mathrm{mod}}\bigr),
\]
exists for every modular Koszul chiral algebra, where $\mathbb G_{\mathrm{mod}}$ denotes the completed modular coefficient ring.  In a cyclic minimal model the class determines a Hamiltonian modular master potential
\[
\mathfrak S_{\cA}=\sum_{r\ge 2}\frac{1}{r!}\,\mathrm{Sh}_r(\Theta_{\cA}),
\]
where $\mathrm{Sh}_r(\Theta_{\cA})$ denotes the homogeneous degree-$r$ Taylor coefficient on the tangent space of the minimal model.  We call $\mathrm{Sh}_r(\Theta_{\cA})$ the \emph{arity-$r$ shadow} of the universal class.
\end{definition}

\begin{remark}[Quadratic, cubic, and quartic shadows as arity-$2$, $3$, and $4$ pieces]
\label{rem:nms-hcq-as-arity-shadows}
Since the universal class $\Theta_\cA$ exists (Theorem~\ref{thm:mc2-bar-intrinsic}), the three tensors
\[
H_{\cA},\qquad \mathfrak C_{\cA},\qquad \mathfrak Q_{\cA}
\]
are nothing but the first three nontrivial shadows of $\Theta_{\cA}$:
\[
H_{\cA}=\mathrm{Sh}_2(\Theta_{\cA}),
\qquad
\mathfrak C_{\cA}=\mathrm{Sh}_3(\Theta_{\cA}),
\qquad
\mathfrak Q_{\cA}=\mathrm{Sh}_4(\Theta_{\cA}).
\]
The entire finite-order theory developed below is therefore the visible arity-$\le 4$ face of the universal Maurer--Cartan class.
\end{remark}

\subsection{Quadratic, cubic, and quartic shadows}
\label{subsec:nms-shadow-jets}

\begin{setup}[Finite-dimensional cyclic slice]
\label{setup:nms-cyclic-slice}
Fix a finite-dimensional graded subspace
\[
V_{\cA}\subset H^*(\Defcyc(\cA),\ell_1)
\]
closed under all transferred operations needed through quartic order.  Assume that the cyclic pairing restricts to a nondegenerate quadratic form on $V_{\cA}$; write
\[
H_{\cA}\colon V_{\cA}\xrightarrow{\sim}V_{\cA}^*[-1]
\]
for the induced Hessian, and let $P_{\cA}:=H_{\cA}^{-1}$ denote the propagator.
\end{setup}

\begin{definition}[Shadow jets]
\label{def:nms-shadow-jets}
The \emph{quadratic}, \emph{cubic}, and \emph{quartic} shadows of $\cA$ on $V_{\cA}$ are the tensors determined by the Taylor expansion
\begin{equation}
\label{eq:nms-shadow-potential-expansion}
S_{\cA}^{\le 4}(x)
=
\frac12H_{\cA}(x,x)
+
\frac1{3!}\mathfrak C_{\cA}(x,x,x)
+
\frac1{4!}\mathfrak Q_{\cA}(x,x,x,x).
\end{equation}
Equivalently, if $(V_{\cA},\ell_n^{\mathrm{tr}})$ is the transferred cyclic minimal model, then
\begin{align}
\mathfrak C_{\cA}(x,y,z)
&:= \sum_{\mathrm{cyc}}\langle x,\ell_2^{\mathrm{tr}}(y,z)\rangle,
\label{eq:nms-cubic-shadow}
\\
\mathfrak Q_{\cA}(x_1,x_2,x_3,x_4)
&:= \sum_{\mathrm{cyc}}\langle x_1,\ell_3^{\mathrm{tr}}(x_2,x_3,x_4)\rangle.
\label{eq:nms-quartic-shadow}
\end{align}
Define the quartic obstruction
\begin{equation}
\label{eq:nms-quartic-obstruction-def}
\mathfrak o_{\cA}^{(4)}
:=
\frac12\{\mathfrak C_{\cA},\mathfrak C_{\cA}\}_{H_{\cA}},
\end{equation}
where the bracket is the Hamiltonian bracket induced by the propagator $P_{\cA}$.
\end{definition}

\begin{theorem}[Quartic shadow master equations; \ClaimStatusProvedHere]
\label{thm:nms-shadow-master-equations}
Assume the truncated Hamiltonian $S_{\cA}^{\le 4}$ satisfies the classical master equation modulo quintic terms:
\[
\{S_{\cA}^{\le 4},S_{\cA}^{\le 4}\}_{H_{\cA}}=O(5).
\]
Then the shadow jets satisfy
\begin{align}
\{H_{\cA},\mathfrak C_{\cA}\}_{H_{\cA}} &= 0,
\label{eq:nms-master-cubic}
\\
\{H_{\cA},\mathfrak Q_{\cA}\}_{H_{\cA}} + \mathfrak o_{\cA}^{(4)} &= 0.
\label{eq:nms-master-quartic}
\end{align}
Equivalently, if one writes
\[
\nabla_{H_{\cA}}(X):=\{H_{\cA},X\}_{H_{\cA}},
\]
then
\[
\nabla_{H_{\cA}}\mathfrak C_{\cA}=0,
\qquad
\nabla_{H_{\cA}}\mathfrak Q_{\cA}+\mathfrak o_{\cA}^{(4)}=0.
\]
\end{theorem}

\begin{proof}
Expand the master equation by homogeneous degree.  The cubic term is exactly \eqref{eq:nms-master-cubic}; the quartic term is exactly \eqref{eq:nms-master-quartic}.  No other contributions occur through quartic order.\qedhere
\end{proof}

\begin{construction}[Separating sewing product]
\label{constr:nms-sewing-product}
Let $P_{\cA}=H_{\cA}^{-1}$ be the propagator.  For symmetric tensors $\alpha\in \operatorname{Sym}^p(V_{\cA}^*)$ and $\beta\in \operatorname{Sym}^q(V_{\cA}^*)$, define the \emph{single-edge sewing product}
\[
\alpha\star_{P_{\cA}}\beta\in \operatorname{Sym}^{p+q-2}(V_{\cA}^*)
\]
by contracting one leg of $\alpha$ with one leg of $\beta$ using $P_{\cA}$ and symmetrizing over the remaining external legs.  This is the tensor-level realization of separating clutching by one internal edge.
\end{construction}

\begin{theorem}[Separating boundary recursion through quartic order; \ClaimStatusProvedHere]
\label{thm:nms-separating-boundary-recursion}
Since the shadow jets are the arity-$\le 4$ projections of the bar-intrinsic MC element $\Theta_\cA$ \textup{(}Theorem~\textup{\ref{thm:mc2-bar-intrinsic})}, which satisfies the modular clutching identity, on every separating clutching map $\xi$ one has
\begin{align}
\xi^*H_{\cA}
&=
H_{\cA}\star_{P_{\cA}} H_{\cA},
\label{eq:nms-clutching-H}
\\
\xi^*\mathfrak C_{\cA}
&=
H_{\cA}\star_{P_{\cA}}\mathfrak C_{\cA}
+
\mathfrak C_{\cA}\star_{P_{\cA}} H_{\cA},
\label{eq:nms-clutching-C}
\\
\xi^*\mathfrak Q_{\cA}
&=
H_{\cA}\star_{P_{\cA}}\mathfrak Q_{\cA}
+
\mathfrak C_{\cA}\star_{P_{\cA}}\mathfrak C_{\cA}
+
\mathfrak Q_{\cA}\star_{P_{\cA}}H_{\cA}.
\label{eq:nms-clutching-Q}
\end{align}
\end{theorem}

\begin{proof}
These are the degree-$2$, degree-$3$, and degree-$4$ components of the clutching identity for the universal class:
\[
\xi^*(\Theta_{\cA})=\Theta_{\cA}\star \Theta_{\cA}.
\]
At quartic order only the three displayed contractions survive.\qedhere
\end{proof}

\subsection{The quartic shadow graph cocycle}
\label{subsec:nms-shadow-graph-complex}

\begin{definition}[Quartic shadow graph complex]
\label{def:nms-shadow-graph-complex}
Let $\mathcal G_{\cA}^{\le 4}$ denote the completed span of stable graphs whose vertices are decorated as follows:
\begin{enumerate}[label=\textup{(\roman*)}]
\item a $2$-valent vertex is decorated by the Hessian $H_{\cA}$,
\item a $3$-valent vertex is decorated by the cubic tensor $\mathfrak C_{\cA}$,
\item a $4$-valent vertex is decorated by the quartic tensor $\mathfrak Q_{\cA}$,
\item every internal edge is contracted with the propagator $P_{\cA}$.
\end{enumerate}
Let $d_{\mathrm{graph}}$ be the differential obtained by summing over separating edge insertions together with the internal differential induced by the Hamiltonian bracket with $H_{\cA}$.
\end{definition}

\begin{construction}[The quartic shadow cocycle]
\label{constr:nms-shadow-cocycle}
Define
\begin{equation}
\label{eq:nms-shadow-cocycle}
\Theta_{\cA}^{\le 4}
:=
H_{\cA}+\mathfrak C_{\cA}+\mathfrak Q_{\cA}
\in \mathcal G_{\cA}^{\le 4}.
\end{equation}
\end{construction}

\begin{theorem}[Finite-order realization of the universal class; \ClaimStatusProvedHere]
\label{thm:nms-shadow-cocycle-characterization}
The element $\Theta_{\cA}^{\le 4}$ is a cocycle in $\mathcal G_{\cA}^{\le 4}$ if and only if the quartic shadow master equations \eqref{eq:nms-master-cubic}--\eqref{eq:nms-master-quartic} and the separating boundary recursion \eqref{eq:nms-clutching-H}--\eqref{eq:nms-clutching-Q} hold.
\end{theorem}

\begin{proof}
The graph differential on the one-vertex generators reproduces the three sewing terms of Theorem~\ref{thm:nms-separating-boundary-recursion}; the Hamiltonian part of the differential reproduces Theorem~\ref{thm:nms-shadow-master-equations}.  Matching homogeneous degrees $2$, $3$, and $4$ yields the claim.\qedhere
\end{proof}

\begin{remark}[Tree terms versus obstruction terms]
\label{rem:nms-tree-vs-obstruction}
There are two different quartic descendants of a cubic tensor $\mathfrak C$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item The \emph{tree term}
\[
T_{\mathfrak C}:=\mathfrak C\star_{P}\mathfrak C
\]
records the quartic geometry created by sewing two cubic vertices with one propagator.
\item The \emph{quartic obstruction}
\[
J_{\mathfrak C}:=\frac12\{\mathfrak C,\mathfrak C\}_{H}
\]
records the Hamiltonian failure of a quartic primitive to exist.
\end{enumerate}
These two contractions are conceptually different.  In particular, a family can have nontrivial quartic boundary geometry even when the quartic obstruction vanishes.
\end{remark}

\subsection{The quartic shadow envelope}
\label{subsec:nms-shadow-envelope}

\begin{definition}[Primary--composite quartic shadow envelope]
\label{def:nms-primary-composite-envelope}
Let $\cA$ be strongly generated by primaries
\[
W^{(d_1)},\dots,W^{(d_r)},\qquad d_1<\cdots<d_r.
\]
The \emph{primary--composite quartic shadow envelope} is the graded vector space
\[
E_{\cA}^{[4]}:=V_{\mathrm{prim}}\oplus V_{\mathrm{comp}},
\]
where
\[
V_{\mathrm{prim}}:=\bigoplus_{i=1}^r \mathbb C\,e_i
\]
is the span of the strong generators and $V_{\mathrm{comp}}$ is the span of all quasi-primary projections
\[
\Pi_{\mathrm{qp}}\bigl(:W^{(d_i)}W^{(d_j)}:\bigr)
\]
that occur in the singular or regular parts of pairwise OPEs of strong generators.  It is the minimal envelope on which the quartic shadow calculus closes.
\end{definition}

\begin{proposition}[Quartic closure of the shadow envelope; \ClaimStatusProvedHere]
\label{prop:nms-quartic-closure-envelope}
The local quartic shadow differential and the quartic separating sewing recursion preserve $E_{\cA}^{[4]}$.
\end{proposition}

\begin{proof}
Through quartic order, every local one-vertex contribution comes from a single pairwise OPE of strong generators.  Such an OPE can produce only another strong generator, its descendants, or a normal-ordered bilinear composite.  After quasi-primary projection, descendants are absorbed into the strong-generator/composite span.  No trilinear composite is needed before quintic order.  The boundary terms are obtained by gluing either two cubic vertices or one quartic vertex with one propagator, so they also remain in the same envelope.\qedhere
\end{proof}

\section{The three primitive nonlinear archetypes}
\label{sec:nms-three-archetypes}

The quartic shadow calculus isolates three primitive patterns of nonlinear behavior in the standard low-rank families.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Gaussian}: no nonlinear jet survives through quartic order.
  OPE is abelian: output is vacuum and derivatives of inputs.
  Shadow depth~$\le 2$.
\item \emph{Lie/tree}: a cubic tensor is present, the quartic obstruction vanishes, and quartic nonlinearity appears first on the boundary as a tree term.
  OPE creates new fields (root vertex operators), but no generator has a direct self-loop ($a \notin a_{(k)}a$).  Shadow depth~$3$.
\item \emph{Contact/quartic}: the cubic tensor vanishes on the chosen slice, and the first nonlinear local term is quartic.
  OPE is abelian but a weight deformation activates the quartic shadow.  Shadow depth~$4$.
\end{enumerate}
A fourth pattern, \emph{mixed/infinite} ($r_{\max} = \infty$), arises when a strong generator belongs to its own self-OPE: $T_{(1)}T = 2T$ for Virasoro.  This direct self-referentiality drives an infinite $A_\infty$ cascade
(Proposition~\ref{prop:self-referentiality-criterion}).
At higher rank, lattice vertex algebras achieve finite depths $5, 6, 7, \dotsc$ through independent cusp forms in $M_{r/2}$ (Theorem~\ref{thm:shadow-spectral-correspondence}).
We now compute the three low-rank patterns in the frame families.

\subsection{Heisenberg}
\label{subsec:nms-heisenberg}

\begin{theorem}[Heisenberg exact linearity; \ClaimStatusProvedHere]
\label{thm:nms-heisenberg-exact-linearity}
On the Heisenberg deformation line one has
\[
\mathfrak C_{\mathcal H}=0,
\qquad
\mathfrak o_{\mathcal H}^{(4)}=0,
\qquad
\mathfrak Q_{\mathcal H}=0.
\]
Equivalently,
\[
\Theta_{\mathcal H}^{\le 4}=H_{\mathcal H}.
\]
\end{theorem}

\begin{proof}
On the Heisenberg line the deformation problem is governed by a constant Poisson structure and the corresponding Moyal quantization is exact at first order.  On the bar side, no higher operations $m_n$ with $n\ge 3$ appear on this slice.  Therefore the transferred binary and ternary nonlinear operations vanish, and hence so do the cubic and quartic shadow tensors.\qedhere
\end{proof}

\begin{corollary}[Gaussian boundary law; \ClaimStatusProvedHere]
\label{cor:nms-heisenberg-gaussian-boundary}
For the Heisenberg family the separating boundary recursion is purely Gaussian:
\[
\xi^*H_{\mathcal H}=H_{\mathcal H}\star H_{\mathcal H},
\qquad
\xi^*\mathfrak C_{\mathcal H}=0,
\qquad
\xi^*\mathfrak Q_{\mathcal H}=0.
\]
\end{corollary}

\begin{remark}[Derived center interpretation: Gaussian class]
\label{rem:nms-heisenberg-derived-center}
In the chiral derived center $\cZ^{\mathrm{der}}_{\mathrm{ch}}(\cH_k)$
(Definition~\ref{def:thqg-chiral-derived-center}), the Gaussian
archetype manifests as follows:
the open/closed quartic resonance class
$\mathfrak{R}^{\mathrm{oc}}_4(\cH_k) = 0$
(Theorem~\ref{thm:thqg-oc-quartic-vanishing}(i)),
so the universal bulk is purely quadratic.
The completed platonic datum
$\Pi^{\mathrm{oc}}_X(\cH_k)$ reduces to the linear holographic
transform $\mathbb{H}_X(\cH_k)$ of
\S\ref{subsec:frontier-protected-holographic-transform}.
\end{remark}

\subsection{Affine \texorpdfstring{$\widehat{\mathfrak{sl}}_2$}{sl2}}
\label{subsec:nms-affine-sl2}

\begin{definition}[Strict current-level sector]
\label{def:nms-affine-sector}
For the affine current algebra $\widehat{\mathfrak{sl}}_{2,k}$, let
\[
V_{\mathrm{aff}}:=\mathfrak{sl}_2[1]\oplus \mathbb C\,K[1]
\]
be the strict current-level sector generated by the current algebra and the level direction.
\end{definition}

\begin{theorem}[Affine cubic normal form; \ClaimStatusProvedHere]
\label{thm:nms-affine-cubic-normal-form}
On the strict current-level sector one has
\[
\mathfrak C_{\mathrm{aff}}(x,y,z)=\kappa(x,[y,z]),
\qquad
\mathfrak o_{\mathrm{aff}}^{(4)}=0.
\]
Consequently there exists a quartic gauge in which
\[
\mathfrak Q_{\mathrm{aff}}=0,
\qquad
\Theta_{\mathrm{aff}}^{\le 4}=H_{\mathrm{aff}}+\mathfrak C_{\mathrm{aff}}.
\]
\end{theorem}

\begin{proof}
The simple pole in the current algebra OPE is the Lie bracket, and the double pole is the invariant bilinear form.  Therefore the cubic Hamiltonian on the strict sector is the cyclic Lie Hamiltonian
\[
\frac16\kappa(a,[a,a]).
\]
The Hamiltonian self-bracket of this cubic term is the Jacobiator, which vanishes identically.  Thus the quartic obstruction vanishes.  Through quartic order one may therefore choose the minimal gauge in which no local quartic vertex remains.\qedhere
\end{proof}

\begin{corollary}[Boundary-generated quartic nonlinearity; \ClaimStatusProvedHere]
\label{cor:nms-affine-boundary-tree}
Even though the local quartic vertex vanishes on the strict current-level sector, the quartic boundary shadow is generally nonzero:
\[
\xi^*\mathfrak Q_{\mathrm{aff}}=\mathfrak C_{\mathrm{aff}}\star_{P_{\mathrm{aff}}}\mathfrak C_{\mathrm{aff}}.
\]
Explicitly,
\[
(\mathfrak C_{\mathrm{aff}}\star_{P_{\mathrm{aff}}}\mathfrak C_{\mathrm{aff}})(x_1,x_2,x_3,x_4)
=
\frac{1}{k_{\mathrm{eff}}}
\sum_{\mathrm{channels}}
\kappa([x_i,x_j],[x_k,x_\ell]),
\]
where $k_{\mathrm{eff}}$ is the normalization of the Hessian on the strict sector.
\end{corollary}

\begin{proof}
Apply the quartic boundary recursion with $\mathfrak Q_{\mathrm{aff}}=0$.  The displayed formula is the definition of sewing two cubic current vertices with one propagator.\qedhere
\end{proof}

\begin{conjecture}[Critical-level emergence; \ClaimStatusConjectured]
\label{thm:nms-critical-level-emergence}
For affine Kac--Moody $\widehat{\mathfrak{g}}_k$, assume the ambient complementarity package exists.  At the critical level $k = -h^\vee$, the quadratic/Hessian shadow vanishes:
\[
H_{\widehat{\mathfrak{g}}_{-h^\vee}} = 0,
\]
while the cubic shadow survives:
\[
\mathfrak C_{\widehat{\mathfrak{g}}_{-h^\vee}}(x,y,z) = \kappa(x,[y,z]).
\]
The complementarity potential is therefore cubic at leading order:
\[
S_{\widehat{\mathfrak{g}}_{-h^\vee}}(a) = \tfrac16\kappa(a,[a,a]) + O(a^4).
\]
\end{conjecture}

\begin{proof}[Proof sketch]
The quadratic part is governed by the shifted-level factor $k + h^\vee$, which vanishes at the critical level.  The simple-pole bracket remains, so the first surviving homogeneous term is the Lie-theoretic cubic tensor.\qedhere
\end{proof}

\begin{conjecture}[Critical self-duality as Maurer--Cartan; \ClaimStatusConjectured]
\label{cor:nms-critical-mc}
At the critical level, the derived self-intersection of the two modular Lagrangians has leading critical equation
\[
[a,a] = 0.
\]
The cubic truncation of the derived critical locus is the Maurer--Cartan locus for the underlying Lie bracket.
\end{conjecture}

\begin{proof}
Differentiate the critical-level cubic action: $dS(a) = \frac12[a,a] + O(a^3)$.  The cubic truncation of $\mathrm{Crit}(S)$ is therefore $\{a : [a,a] = 0\}$, which is the Maurer--Cartan locus.\qedhere
\end{proof}

\begin{remark}[Critical level is purely nonlinear]
\label{rem:nms-critical-purely-nonlinear}
The critical level is not ``more linear'' than generic level.  It is the opposite: at the critical level, complementarity becomes purely nonlinear at leading order.  This provides the first bridge from complementarity geometry to critical-level representation theory (the Feigin--Frenkel center).
\end{remark}

\begin{remark}[Derived center interpretation: Lie/tree class]
\label{rem:nms-affine-derived-center}
In the chiral derived center, the cubic shadow
$\mathfrak{C}_{\mathrm{aff}} \in \cZ^1$ is a degree-$1$
Gerstenhaber algebra element (a bulk derivation), and the quartic
contact vanishes in the standard gauge:
$[\mathfrak{Q}^{\mathrm{ct}}_{\mathrm{aff}}] = 0$ in $\cZ^2$.
The open/closed quartic resonance class reduces to the tree correction:
$\mathfrak{R}^{\mathrm{oc}}_4(\widehat{\mathfrak{g}}_k)
= [\mathfrak{C} \star_{P} \mathfrak{C}] \in \cZ^2$
(Theorem~\ref{thm:thqg-oc-quartic-vanishing}(ii)).
This is the trace of cubic graviton exchange across a boundary node.
\end{remark}

\subsection{The \texorpdfstring{$\beta\gamma$}{betagamma} system}
\label{subsec:nms-betagamma}

\begin{definition}[Weight/contact slice]
\label{def:nms-betagamma-slice}
Let $V_{\beta\gamma}$ be the minimal cyclic slice generated by the explicit weight-changing deformation class and the first contact class detected by the first nontrivial higher operation $m_3$.
\end{definition}

\begin{theorem}[\texorpdfstring{$\beta\gamma$}{betagamma} quartic birth; \ClaimStatusProvedHere]
\label{thm:nms-betagamma-quartic-birth}
On the weight/contact slice one has
\[
\mathfrak C_{\beta\gamma}=0,
\qquad
\mathfrak o_{\beta\gamma}^{(4)}=0,
\qquad
\mathfrak Q_{\beta\gamma}=\operatorname{cyc}(m_3).
\]
Equivalently, the first nonlinear local shadow is quartic rather than cubic.  Writing $\eta$ for the weight-changing class,
\[
\mathfrak Q_{\beta\gamma}(\eta,\eta,\eta,\eta)
=
\mu_{\beta\gamma},
\qquad
\mu_{\beta\gamma}:=\langle \eta,m_3(\eta,\eta,\eta)\rangle.
\]
\end{theorem}

\begin{proof}
On the explicit weight-changing line the Maurer--Cartan equation is linear, so no cubic term is produced on that slice.  The first displayed higher operation in the bar model is $m_3$, and in a cyclic Hamiltonian an $m_3$-operation contributes quartically.  Therefore the first local nonlinear term is quartic.  Since the cubic term vanishes, the quartic obstruction vanishes identically.\qedhere
\end{proof}

\begin{corollary}[Vanishing of the quartic contact invariant; \ClaimStatusProvedHere]
\label{cor:nms-betagamma-mu-vanishing}
On the weight-changing line of the $\beta\gamma$ system,
\[
  \mu_{\beta\gamma} := \langle \eta,\, m_3(\eta,\eta,\eta) \rangle = 0.
\]
The quartic contact invariant vanishes identically on the weight-changing
deformation.
\end{corollary}

\begin{proof}
Two independent arguments.
(1)~Homotopy transfer: the transferred bracket satisfies
$m_2(\eta,\eta) = 0$ (the Maurer--Cartan equation on the one-dimensional
weight-changing subspace is linear), so
$m_3(\eta,\eta,\eta) = 0$ by the $A_\infty$ relation
$m_3 = m_2 \circ (h \otimes \mathrm{id}) \circ m_2 + \cdots$
applied to the vanishing binary input.
(2)~Rank-one abelian rigidity (Theorem~\ref{thm:nms-rank-one-rigidity}):
the weight-changing line is a one-dimensional cyclic subspace with
vanishing higher brackets.
Computational verification: \texttt{compute/lib/betagamma\_quartic\_contact.py}.
\end{proof}

\begin{corollary}[Pure contact boundary law; \ClaimStatusProvedHere]
\label{cor:nms-betagamma-boundary-law}
On the weight/contact slice of $\beta\gamma$ one has
\[
\xi^*\mathfrak Q_{\beta\gamma}
=
H_{\beta\gamma}\star_{P_{\beta\gamma}}\mathfrak Q_{\beta\gamma}
+
\mathfrak Q_{\beta\gamma}\star_{P_{\beta\gamma}}H_{\beta\gamma}.
\]
There is no cubic tree contribution.
\end{corollary}

\begin{proof}
Apply the quartic boundary recursion with $\mathfrak C_{\beta\gamma}=0$.\qedhere
\end{proof}

\begin{theorem}[Primitive nonlinear archetype trichotomy; \ClaimStatusProvedHere]
\label{thm:nms-archetype-trichotomy}
Through quartic order, the three frame families realize the three primitive nonlinear archetypes:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Heisenberg is Gaussian:
\[
\Theta_{\mathcal H}^{\le 4}=H_{\mathcal H}.
\]
\item Affine $\widehat{\mathfrak{sl}}_2$ is of Lie/tree type:
\[
\Theta_{\mathrm{aff}}^{\le 4}=H_{\mathrm{aff}}+\mathfrak C_{\mathrm{aff}},
\]
with quartic boundary term generated by $\mathfrak C_{\mathrm{aff}}\star \mathfrak C_{\mathrm{aff}}$.
\item The $\beta\gamma$ system is of contact/quartic type:
\[
\Theta_{\beta\gamma}^{\le 4}=H_{\beta\gamma}+\mathfrak Q_{\beta\gamma},
\]
with quartic boundary term propagated from the local quartic vertex.
\end{enumerate}
\end{theorem}

\begin{proof}
The three cases follow from the explicit shadow computations:
Heisenberg shadow Gaussianity (Theorem~\ref{thm:nms-heisenberg-exact-linearity}),
affine cubic normal form (Theorem~\ref{thm:nms-affine-cubic-normal-form}),
and $\beta\gamma$ quartic birth (Theorem~\ref{thm:nms-betagamma-quartic-birth}).
\end{proof}

\begin{theorem}[Rank-one abelian rigidity; \ClaimStatusProvedHere]
\label{thm:nms-rank-one-rigidity}
Let $L \subset V_{\cA}$ be a one-dimensional cyclic subspace on which all transferred higher brackets vanish:
\[
\ell_n^{\mathrm{tr}}\big|_L = 0 \qquad (n \ge 2).
\]
Then the restriction of the complementarity potential to $L$ is exactly quadratic.  In particular, complementarity on $L$ is formally fake.
\end{theorem}

\begin{proof}
On such a line the cyclic action expansion collapses to its quadratic Hessian part: every higher jet $\mathrm{Sh}_r(\Theta_{\cA})|_L$ for $r \ge 3$ involves at least one factor of some $\ell_n^{\mathrm{tr}}$ with $n \ge 2$, and all vanish.\qedhere
\end{proof}

\begin{remark}[Uniform explanation of linear examples]
\label{rem:nms-uniform-linearity}
Theorem~\ref{thm:nms-rank-one-rigidity} explains uniformly why the Heisenberg level line and the explicit $\beta\gamma$ weight-shift line are both formally linear: in each case the deformation lies on a one-dimensional sector with vanishing higher brackets.  Real nonlinear complementarity requires either a non-abelian bracket (as for affine $\widehat{\mathfrak{sl}}_2$) or a higher-dimensional deformation space (as for $\beta\gamma$ off the weight-shift line).
\end{remark}

\begin{remark}[Derived center interpretation: contact class]
\label{rem:nms-betagamma-derived-center}
In the chiral derived center, the contact archetype exhibits a
subtle collapse: $\mathfrak{C}_{\beta\gamma} = 0$ (no cubic shadow),
so the tree correction vanishes, and the quartic contact class
$[\mathfrak{Q}^{\mathrm{ct}}_{\beta\gamma}] \in \cZ^2$ is the
sole contributor to $\mathfrak{R}^{\mathrm{oc}}_4$.
On the weight-changing line, rank-one abelian rigidity
(Corollary~\ref{cor:nms-betagamma-mu-vanishing}) collapses this
class to zero:
$\mathfrak{R}^{\mathrm{oc}}_4(\beta\gamma)|_{\text{wt-line}} = 0$
(Theorem~\ref{thm:thqg-oc-quartic-vanishing}(iii)).
The contact depth $r_{\max} = 4$ is a stratum phenomenon, not a bulk
gravitational invariant.
\end{remark}

\section{Mixed cubic--quartic families: Virasoro and principal \texorpdfstring{$\mathcal W_N$}{WN}}
\label{sec:nms-mixed-families}

The three primitive archetypes are not the end of the story.  Virasoro and principal $\mathcal W_N$ introduce the first genuinely mixed families, in which cubic and quartic nonlinearities coexist already at the first nontrivial level.

\subsection{A universal cubic sector for strong generators}
\label{subsec:nms-universal-cubic-sector}

\begin{theorem}[Universal gravitational cubic tensor; \ClaimStatusProvedHere]
\label{thm:nms-universal-gravitational-cubic}
Let $\cA$ be strongly generated by Virasoro-primary fields
\[
W^{(2)}=T,\;W^{(d_2)},\dots,W^{(d_r)}
\]
of conformal weights $2,d_2,\dots,d_r$.  On the primary slice with coordinates $x_2,x_{d_2},\dots,x_{d_r}$ dual to the strong generators, the cubic shadow contains the universal summand
\begin{equation}
\label{eq:nms-universal-gravitational-cubic}
\mathfrak C^{\mathrm{grav}}_{\cA}
=
2x_2^3+\sum_{i\ge 2} d_i\,x_2x_{d_i}^2.
\end{equation}
\end{theorem}

\begin{proof}
Each $W^{(d_i)}$ is Virasoro-primary of weight $d_i$, so
\[
T_{(1)}W^{(d_i)}=d_i\,W^{(d_i)}.
\]
For $T$ itself this gives $T_{(1)}T=2T$.  The cyclic cubic tensor is obtained by pairing the output of this action with the quadratic pairing and then symmetrizing the three legs.  This produces exactly the stated universal cubic terms.\qedhere
\end{proof}

\subsection{Virasoro}
\label{subsec:nms-virasoro}

\begin{definition}[Virasoro quartic shadow envelope]
\label{def:nms-virasoro-envelope}
Let
\[
\Lambda_{\mathrm{Vir}}:=:TT:-\frac{3}{10}\partial^2T.
\]
The Virasoro quartic shadow envelope is
\[
E^{[4]}_{\mathrm{Vir}}:=\mathbb C\langle T,\Lambda_{\mathrm{Vir}}\rangle.
\]
\end{definition}

\begin{theorem}[Virasoro mixed shadow theorem; \ClaimStatusProvedHere]
\label{thm:nms-virasoro-mixed-shadow}
On $E^{[4]}_{\mathrm{Vir}}$ one has
\[
H_{\mathrm{Vir}}=\frac{c}{2}x^2,
\qquad
\mathfrak C_{\mathrm{Vir}}=2x^3,
\qquad
\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}}\neq 0.
\]
Equivalently,
\[
\Theta_{\mathrm{Vir}}^{\le 4}=H_{\mathrm{Vir}}+\mathfrak C_{\mathrm{Vir}}+\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}}.
\]
\end{theorem}

\begin{proof}
The quadratic term is the quartic pole of the $TT$ OPE,
\[
T(z)T(w)\sim \frac{c/2}{(z-w)^4}+\cdots.
\]
The cubic term is the conformal-weight channel
\[
T_{(1)}T=2T,
\]
which is the rank-one case of Theorem~\ref{thm:nms-universal-gravitational-cubic}.  The regular term $:TT:$ is not quasi-primary, but its corrected quasi-primary projection is $\Lambda_{\mathrm{Vir}}$, which therefore contributes a genuine one-vertex quartic contact term.\qedhere
\end{proof}

\begin{theorem}[Explicit Virasoro quartic contact coefficient; \ClaimStatusProvedHere]
\label{thm:nms-virasoro-quartic-explicit}
\index{quartic contact!Virasoro explicit coefficient}
The quartic contact coefficient of the Virasoro shadow envelope is
\begin{equation}
\label{eq:nms-virasoro-quartic-explicit}
\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}}
= \frac{10}{c(5c+22)}.
\end{equation}
This is the first non-abelian Ring~$2$ shadow coefficient to be
extracted in closed form.
\end{theorem}

\begin{proof}
\emph{Step~1} (Quasi-primary Gram matrix).
The vacuum-module states at level~$4$ are
$|1\rangle = L_{-4}|0\rangle$ and
$|2\rangle = L_{-2}^2|0\rangle$, with Gram matrix
\[
G = \begin{pmatrix} 5c & 3c \\ 3c & c(c+8)/2 \end{pmatrix}
\]
computed from $[L_4, L_{-4}] = 8L_0 + 5c$,
$\langle 0|L_4 L_{-2}^2|0\rangle = 3c$, and
$\langle 0|L_2^2 L_{-2}^2|0\rangle = c(c+8)/2$.

\emph{Step~2} (Quasi-primary projection).
The condition $L_1 \Lambda_{\mathrm{Vir}} = 0$ determines
$\Lambda = L_{-2}^2|0\rangle - a\,L_{-4}|0\rangle$ with
$a = 3/5$ (from $L_1 L_{-2}^2|0\rangle = 3L_{-3}|0\rangle$
and $L_1 L_{-4}|0\rangle = 5L_{-3}|0\rangle$).

\emph{Step~3} (BPZ norm).
\[
\langle\Lambda|\Lambda\rangle
= G_{22} - 2a\,G_{12} + a^2\,G_{11}
= \frac{c(c+8)}{2} - \frac{6}{5}\cdot 3c + \frac{9}{25}\cdot 5c
= \frac{c(5c+22)}{10}.
\]

\emph{Step~4} (Contact coefficient).
The $TT$ OPE at level~$0$ (regular part) contains
$\Lambda_{\mathrm{Vir}}$ with coefficient~$1$
(by definition of normal ordering $:TT:$ and the projection to
$\Lambda$).  The quartic contact coefficient is therefore
$1/\langle\Lambda|\Lambda\rangle = 10/[c(5c+22)]$.

Computational verification:
\texttt{compute/lib/virasoro\_quartic\_contact.py} ($28$~tests).
\end{proof}

\begin{remark}[Significance for the $\Theta_\cA$ programme]
\label{rem:quartic-theta-significance}
The quartic contact coefficient
$\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}} = 10/[c(5c+22)]$
is the arity-$4$ Taylor jet of the complementarity potential
$S_{\mathrm{Vir}}$ around the scalar $\kappa(\mathrm{Vir}_c) = c/2$.
Together with the scalar $\kappa$ (arity~$2$) and the cubic
$\mathfrak C = 2$ (arity~$3$), it provides the first three terms of
the Taylor expansion of $\Theta_{\mathrm{Vir}}$.

The singular locus $c(5c+22) = 0$ consists of:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $c = 0$: the uncurved point where
  $\kappa = 0$ (Corollary~\textup{\ref{cor:nms-virasoro-cubic-leading}});
\item $c = -22/5$: the Lee--Yang value
  $c_{5,2} = 1 - 6 \cdot 9/10 = -22/5$, where the Kac determinant
  at level~$4$ vanishes and $\Lambda$ becomes null.
\end{enumerate}
The formula is well-defined and positive for all non-degenerate
generic~$c > 0$.
\end{remark}

\begin{corollary}[Cubic-leading Virasoro at the uncurved point; \ClaimStatusProvedHere]
\label{cor:nms-virasoro-cubic-leading}
At $c=0$ the quadratic term of the Virasoro shadow vanishes while the cubic term survives:
\[
H_{\mathrm{Vir}}=0,
\qquad
\mathfrak C_{\mathrm{Vir}}\neq 0.
\]
Hence the leading complementarity potential is cubic, with quartic contact correction.
\end{corollary}

\begin{proof}
This is immediate from Theorem~\ref{thm:nms-virasoro-mixed-shadow}.\qedhere
\end{proof}

\begin{remark}[Derived center interpretation: mixed class]
\label{rem:nms-virasoro-derived-center}
The mixed archetype is the first where the derived center carries
irreducibly nonlinear gravitational data.  In $\cZ^2$, both the
quartic contact class
$[\mathfrak{Q}^{\mathrm{ct}}_{\mathrm{Vir}}]
= [10/(c(5c+22))] \cdot x^4$
and the tree correction
$[\mathfrak{C}_{\mathrm{Vir}} \star_{P_{\mathrm{Vir}}}
\mathfrak{C}_{\mathrm{Vir}}]$ are nonzero, so
$\mathfrak{R}^{\mathrm{oc}}_4(\mathrm{Vir}_c) \neq 0$ for
generic~$c$
(Theorem~\ref{thm:thqg-oc-quartic-vanishing}(iv)).
The poles at $c = 0$ and $c = -22/5$ (null-state divisor) are the
first instances where the bulk gravitational dynamics degenerates.
The nonvanishing quintic obstruction
$o^{(5)}_{\mathrm{Vir}} = \{\mathfrak{C}, \mathfrak{Q}\}_H \neq 0$
forces the full Gerstenhaber algebra on $\cZ^*$ to be
non-formally-generated: no finite truncation of the shadow tower
captures the complete bulk dynamics.  For the $\cW_3$ algebra,
the quartic resonance divisor acquires the additional factor
$c(2c-1)(5c+22) = 0$, detecting the Ising model $c = 1/2$ and the
Yang--Lee edge $c = -22/5$ as gravitational degeneration points.
\end{remark}

\subsection{The prototype higher-spin family \texorpdfstring{$\mathcal W_3$}{W3}}
\label{subsec:nms-w3}

\begin{definition}[\texorpdfstring{$\mathcal W_3$}{W3} quartic shadow envelope]
\label{def:nms-w3-envelope}
Let $T$ and $W$ denote the strong generators of $\mathcal W_3$, let
\[
\Lambda=:TT:-\frac{3}{10}\partial^2T
\]
be the weight-$4$ quasi-primary composite, and let $\Lambda_2,\Lambda_3$ denote the two weight-$6$ quasi-primary composites extracted from the regular part of the $W$--$W$ OPE.  Define
\[
E^{[4]}_{W_3}:=\mathbb C\langle T,W,\Lambda,\Lambda_2,\Lambda_3\rangle.
\]
\end{definition}

\begin{theorem}[\texorpdfstring{$\mathcal W_3$}{W3} mixed-shadow normal form; \ClaimStatusProvedHere]
\label{thm:nms-w3-mixed-shadow-normal-form}
On $E^{[4]}_{W_3}$ one has
\[
H_{W_3}=\frac c2\,t^2+\frac c3\,w^2,
\qquad
\mathfrak C^{\mathrm{grav}}_{W_3}=2t^3+3tw^2.
\]
Moreover the quartic contact sector is nonzero and contains:
\begin{enumerate}[label=\textup{(\roman*)}]
\item a weight-$4$ contact channel through $\Lambda$, with coefficient proportional to $\frac{16}{22+5c}$;
\item a weight-$6$ contact channel through the quasi-primary square of $W$ and the composites $\Lambda_2,\Lambda_3$.
\end{enumerate}
In particular,
\[
\Theta_{W_3}^{\le 4}=H_{W_3}+\mathfrak C_{W_3}+\mathfrak Q_{W_3}^{\mathrm{contact}}
\]
is genuinely mixed cubic--quartic.
\end{theorem}

\begin{proof}
The diagonal Hessian comes from the leading self-poles
\[
T_{(3)}T=\frac c2,
\qquad
W_{(5)}W=\frac c3.
\]
The universal cubic term is Theorem~\ref{thm:nms-universal-gravitational-cubic} specialized to the weights $2$ and $3$.  The nonlinear $W$--$W$ OPE produces the weight-$4$ quasi-primary $\Lambda$ with coefficient $16/(22+5c)$ and also yields the weight-$6$ quasi-primary composites through the regular part.  These are local quartic contact vertices.\qedhere
\end{proof}

\begin{definition}[Primary quartic resonance divisor for \texorpdfstring{$\mathcal W_3$}{W3}]
\label{def:nms-w3-primary-resonance}
Let
\[
\Xi_W:=\Pi_{\mathrm{qp}}(:W^2:)
\]
be the quasi-primary square of the spin-$3$ generator.  The \emph{primary quartic resonance divisor} of $\mathcal W_3$ is the vanishing locus of the rank-one Gram pairing of $\Xi_W$.
\end{definition}

\begin{proposition}[Visible quartic resonance factor for \texorpdfstring{$\mathcal W_3$}{W3}; \ClaimStatusProvedHere]
\label{prop:nms-w3-visible-resonance-factor}
The norm of $\Xi_W$ has the form
\[
\langle \Xi_W(z),\Xi_W(w)\rangle
=
\frac{\mathrm{const}\cdot c^2(2c-1)(5c+22)}{(z-w)^{12}},
\]
so the visible rank-one quartic resonance divisor contains
\[
\mathcal R^{\mathrm{vis}}_4(W_3)=\{c(2c-1)(5c+22)=0\}.
\]
\end{proposition}

\begin{proof}
This is the explicit quasi-primary square computation in the $W_3$ composite-field sector.  The coefficient is basis-independent in rank one, so its vanishing gives a canonical divisor on the parameter line.\qedhere
\end{proof}

\begin{remark}[Visible versus full quartic resonance]
\label{rem:nms-visible-vs-full-resonance}
The divisor of Proposition~\ref{prop:nms-w3-visible-resonance-factor} is a visible component of the full quartic resonance locus.  The full resonance divisor of the entire composite sector may acquire additional components from the larger Gram matrix of $\Lambda$, $\Lambda_2$, $\Lambda_3$, and any further quartic composites appearing on the chosen slice.
\end{remark}

\subsection{Principal \texorpdfstring{$\mathcal W_N$}{WN}}
\label{subsec:nms-principal-wn}

\begin{definition}[Principal quartic shadow envelope]
\label{def:nms-principal-wn-envelope}
For principal $\mathcal W_N$ with strong generators
\[
W^{(2)}=T,\;W^{(3)},\dots,W^{(N)},
\]
let $E_{W_N}^{[4]}$ be the primary--composite quartic shadow envelope generated by the strong generators together with all quasi-primary bilinears
\[
\Pi_{\mathrm{qp}}\bigl(:W^{(r)}W^{(s)}:\bigr)
\qquad (2\le r\le s\le N)
\]
that occur in pairwise OPEs.
\end{definition}

\begin{theorem}[Diagonal Hessian and universal cubic sector for principal \texorpdfstring{$\mathcal W_N$}{WN}; \ClaimStatusProvedHere]
\label{thm:nms-principal-wn-hessian-cubic}
On the primary slice of principal $\mathcal W_N$ with coordinates $x_2,\dots,x_N$ one has
\[
H_{W_N}=\sum_{s=2}^N\frac{c}{s}x_s^2,
\qquad
\mathfrak C^{\mathrm{grav}}_{W_N}=2x_2^3+\sum_{s=3}^N s\,x_2x_s^2.
\]
\end{theorem}

\begin{proof}
The diagonal Hessian comes from the leading self-poles
\[
W^{(s)}_{(2s-1)}W^{(s)}=\frac cs,
\]
while distinct conformal weights contribute no vacuum cross-term.  The universal cubic sector is Theorem~\ref{thm:nms-universal-gravitational-cubic}.\qedhere
\end{proof}

\begin{theorem}[Nonvanishing of contact quartics for principal \texorpdfstring{$\mathcal W_N$}{WN}; \ClaimStatusProvedHere]
\label{thm:nms-principal-wn-contact-nonvanishing}
For every principal $\mathcal W_N$ with $N\ge 3$, the contact quartic sector is nonzero:
\[
\mathfrak Q_{W_N}^{\mathrm{contact}}\neq 0.
\]
\end{theorem}

\begin{proof}
For each $s\ge 3$, the field $W^{(s)}$ has nonzero two-point function and nonzero leading self-pole.  Its normal-ordered square therefore has a nontrivial quasi-primary projection
\[
\Lambda_s:=\Pi_{\mathrm{qp}}(:W^{(s)}W^{(s)}:),
\]
which belongs to the quartic shadow envelope.  These quasi-primary squares contribute local quartic contact terms.\qedhere
\end{proof}

\begin{corollary}[Principal \texorpdfstring{$\mathcal W_N$}{WN} is mixed cubic--quartic; \ClaimStatusProvedHere]
\label{cor:nms-principal-wn-mixed}
For every principal $\mathcal W_N$ with $N\ge 3$ and generic parameter,
\[
\Theta_{W_N}^{\le 4}
=
H_{W_N}+\mathfrak C^{\mathrm{grav}}_{W_N}+\mathfrak C^{\mathrm{hs}}_{W_N}+\mathfrak Q^{\mathrm{contact}}_{W_N},
\]
with both the cubic and the quartic local sectors nonzero.
\end{corollary}

\begin{proof}
The cubic sector is nonzero by Theorem~\ref{thm:nms-principal-wn-hessian-cubic}.  The contact quartic sector is nonzero by Theorem~\ref{thm:nms-principal-wn-contact-nonvanishing}.\qedhere
\end{proof}

\section{From Gram determinants to a modular quartic resonance class}
\label{sec:nms-modular-resonance-class}

We now promote the quartic resonance divisor from a polynomial in the parameter to a modular characteristic class.  The central idea is simple.  A Gram determinant depends on a choice of basis, but its determinant line does not.  The correct modular invariant is therefore not the determinant function itself but the determinant \emph{section} of a canonical line bundle.  Its vanishing is the resonance locus.  The clutching law for this section is the first nonlinear shadow of the clutching identity for $\Theta_{\cA}$.

\subsection{The determinant line of the contact quartic sector}
\label{subsec:nms-determinant-line}

\begin{definition}[Generic quartic-regular parameter locus]
\label{def:nms-generic-parameter-locus}
Let $\cA$ be a family of strongly generated chiral algebras depending algebraically on a parameter $u$ (for example level or central charge).  Let $B_{\cA}^{\circ}$ denote the maximal Zariski-open locus on which the ranks of all weight-graded contact quartic spaces are locally constant.  All bundles below are defined over $\overline{\mathcal M}_{g,n}\times B_{\cA}^{\circ}$.
\end{definition}

\begin{definition}[Weight-graded contact quartic bundle]
\label{def:nms-contact-quartic-bundle}
Let
\[
\mathscr E_{g,n}^{[4]}(\cA)
\]
denote the quartic shadow local system obtained by transporting the fiberwise envelope $E_{\cA}^{[4]}$ along the factorization family over $\overline{\mathcal M}_{g,n}\times B_{\cA}^{\circ}$.  For each total conformal weight $d$, let
\[
\mathscr C_{g,n}^{\mathrm{ct},d}(\cA)
\subset
\mathscr E_{g,n}^{[4]}(\cA)
\]
be the locally free subsheaf generated by zero-internal-edge quasi-primary bilinear composites of total weight $d$.  Put
\[
\mathscr C_{g,n}^{\mathrm{ct}}(\cA):=\bigoplus_d \mathscr C_{g,n}^{\mathrm{ct},d}(\cA).
\]
For each $d$, let $\mathscr U_{g,n}^{(d)}$ denote the tautological modular line in which weight-$d$ two-point functions transform.
\end{definition}

\begin{remark}[About the tautological lines]
\label{rem:nms-tautological-lines}
The precise expression for $\mathscr U_{g,n}^{(d)}$ depends on the chosen presentation of the factorization theory; it is the standard modular line attached to a weight-$d$ quasi-primary insertion.  The determinant construction below is independent of any trivialization of these lines.  In genus $0$ and after choosing the standard coordinate trivialization, the determinant section becomes an honest polynomial in the parameter.
\end{remark}

\begin{construction}[Gram determinant line]
\label{constr:nms-gram-determinant-line}
For each weight $d$, let
\[
q_{g,n}^{(d)}(\cA)
\colon
\mathscr C_{g,n}^{\mathrm{ct},d}(\cA)\otimes
\mathscr C_{g,n}^{\mathrm{ct},d}(\cA)
\longrightarrow
\mathscr U_{g,n}^{(d)}
\]
be the symmetric bilinear form given by the genus-$(g,n)$ two-point function on the contact quartic sector.  Set
\begin{equation}
\label{eq:nms-resonance-line}
\mathscr L_{4,g,n}^{\mathrm{res}}(\cA)
:=
\bigotimes_d
\Bigl(
(\det \mathscr C_{g,n}^{\mathrm{ct},d}(\cA))^{-\otimes 2}
\otimes
(\mathscr U_{g,n}^{(d)})^{\otimes r_d}
\Bigr),
\end{equation}
where $r_d:=\operatorname{rk}(\mathscr C_{g,n}^{\mathrm{ct},d}(\cA))$.  The determinant of the weight-$d$ Gram form defines a section
\[
\det q_{g,n}^{(d)}(\cA)
\in
\Gamma\Bigl(\overline{\mathcal M}_{g,n}\times B_{\cA}^{\circ},
(\det \mathscr C_{g,n}^{\mathrm{ct},d}(\cA))^{-\otimes 2}
\otimes
(\mathscr U_{g,n}^{(d)})^{\otimes r_d}
\Bigr).
\]
Their tensor product is the \emph{quartic resonance section}
\begin{equation}
\label{eq:nms-resonance-section}
s_{4,g,n}^{\mathrm{res}}(\cA)
:=
\bigotimes_d \det q_{g,n}^{(d)}(\cA)
\in \Gamma\bigl(\overline{\mathcal M}_{g,n}\times B_{\cA}^{\circ},
\mathscr L_{4,g,n}^{\mathrm{res}}(\cA)\bigr).
\end{equation}
\end{construction}

\begin{definition}[Modular quartic resonance class]
\label{def:nms-modular-quartic-resonance-class}
The \emph{modular quartic resonance class} of $\cA$ in genus $(g,n)$ is the Cartier divisor class
\begin{equation}
\label{eq:nms-modular-resonance-class}
\mathfrak R_{4,g,n}^{\mathrm{mod}}(\cA)
:=
\operatorname{div}\bigl(s_{4,g,n}^{\mathrm{res}}(\cA)\bigr)
\in
\operatorname{Pic}\bigl(\overline{\mathcal M}_{g,n}\times B_{\cA}^{\circ}\bigr).
\end{equation}
\end{definition}

\begin{proposition}[Basis independence and specialization; \ClaimStatusProvedHere]
\label{prop:nms-basis-independence-specialization}
The section $s_{4,g,n}^{\mathrm{res}}(\cA)$ and its divisor class are independent of every choice of local basis of the contact quartic bundle.  When $g=n=0$ and the tautological lines are trivialized in the standard coordinate chart, the zero locus of $s_{4,0,0}^{\mathrm{res}}(\cA)$ is exactly the Gram-determinant resonance divisor of the quartic contact sector.
\end{proposition}

\begin{proof}
Under a basis change by a matrix $A$, the Gram matrix transforms by
\[
G\longmapsto A^{\mathsf T}GA.
\]
Therefore its determinant transforms by the square of the determinant of $A$, which is precisely compensated by the determinant-line factor in \eqref{eq:nms-resonance-line}.  Thus the determinant section is basis-independent.  In genus $0$ and in a trivializing coordinate chart, the tautological lines become trivial and the determinant section becomes the ordinary Gram determinant.\qedhere
\end{proof}

\begin{remark}[Why this is a characteristic class]
\label{rem:nms-why-characteristic-class}
The resonance divisor is now attached to a canonical line bundle on the modular parameter space, not to a chosen matrix.  It is functorial under isomorphisms of the family, stable under change of basis, and intrinsic to the factorization transport of the contact quartic sector.  This is why it deserves to be called a modular characteristic class.
\end{remark}

\subsection{The tree bundle and the first nonlinear boundary correction}
\label{subsec:nms-tree-bundle}

\begin{definition}[Cubic tree bundle along a separating boundary]
\label{def:nms-cubic-tree-bundle}
Let
\[
\xi\colon \overline{\mathcal M}_{g_1,n_1+1}\times \overline{\mathcal M}_{g_2,n_2+1}
\longrightarrow \overline{\mathcal M}_{g,n}
\]
be a separating clutching map.  The \emph{cubic tree bundle}
\[
\mathscr T_{3,\xi}(\cA)
\subset
\xi^*\mathscr E_{g,n}^{[4]}(\cA)
\]
is the locally free image of the one-edge sewing map generated by the cubic shadow:
\[
\mathfrak C_{\cA}\star_{P_{\cA}}\mathfrak C_{\cA}.
\]
Its determinant line and determinant section are defined exactly as in Construction~\ref{constr:nms-gram-determinant-line}; write
\[
\mathfrak T_{3,\xi}(\cA)
:=
\operatorname{div}(s_{3,\xi}^{\mathrm{tree}}(\cA))
\]
for the resulting divisor class.
\end{definition}

\begin{remark}[Interpretation of the tree class]
\label{rem:nms-tree-class-interpretation}
The class $\mathfrak T_{3,\xi}(\cA)$ is the boundary contribution created purely by sewing cubic vertices.  It vanishes whenever the cubic shadow vanishes on the chosen slice.  It is the first boundary term that cannot be seen in the quadratic theory.
\end{remark}

\begin{theorem}[Boundary filtration of the quartic envelope; \ClaimStatusProvedHere]
\label{thm:nms-boundary-filtration-quartic-envelope}
On a separating boundary stratum there is a natural increasing filtration
\[
0\subset F^0\subset F^1=\xi^*\mathscr E_{g,n}^{[4]}(\cA)
\]
by internal-edge number such that the associated graded object splits canonically as
\begin{equation}
\label{eq:nms-associated-graded-boundary}
\operatorname{gr}\,\xi^*\mathscr E_{g,n}^{[4]}(\cA)
\cong
p_1^*\mathscr C_{g_1,n_1+1}^{\mathrm{ct}}(\cA)
\oplus
p_2^*\mathscr C_{g_2,n_2+1}^{\mathrm{ct}}(\cA)
\oplus
\mathscr T_{3,\xi}(\cA),
\end{equation}
where $p_1$ and $p_2$ are the two projections.
\end{theorem}

\begin{proof}
At quartic order a vertex on the boundary can have either zero internal edges or one internal edge.  Zero internal edges give the contact quartic sectors transported from the two components.  One internal edge joining two cubic vertices gives the tree sector.  No higher-edge contribution appears before quintic order.  This yields the stated filtration and splitting on the associated graded.\qedhere
\end{proof}

\begin{theorem}[Clutching law for the modular quartic resonance class; \ClaimStatusProvedHere]
\label{thm:nms-clutching-law-modular-resonance}
Let $\cA$ be a strongly generated modular Koszul family over $B_{\cA}^{\circ}$.  Along a separating clutching map $\xi$ one has the divisor identity
\begin{equation}
\label{eq:nms-resonance-clutching-law}
\xi^*\mathfrak R_{4,g,n}^{\mathrm{mod}}(\cA)
=
p_1^*\mathfrak R_{4,g_1,n_1+1}^{\mathrm{mod}}(\cA)
+
p_2^*\mathfrak R_{4,g_2,n_2+1}^{\mathrm{mod}}(\cA)
+
\mathfrak T_{3,\xi}(\cA).
\end{equation}
In words: the boundary restriction of the quartic resonance class is the sum of the two contact resonance classes from the components together with a new tree correction generated by the cubic shadow.
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:nms-boundary-filtration-quartic-envelope}, the associated graded of the pulled-back quartic envelope splits into the two contact bundles and the cubic tree bundle.  The quartic clutching formula
\[
\xi^*\mathfrak Q_{\cA}
=
H_{\cA}\star\mathfrak Q_{\cA}
+
\mathfrak C_{\cA}\star\mathfrak C_{\cA}
+
\mathfrak Q_{\cA}\star H_{\cA}
\]
shows that, on the associated graded, the Gram pairing is block-upper-triangular with diagonal blocks given by the two contact pairings and the tree pairing.  The determinant section therefore factors:
\[
\operatorname{gr}\,\xi^*s_{4,g,n}^{\mathrm{res}}(\cA)
=
p_1^*s_{4,g_1,n_1+1}^{\mathrm{res}}(\cA)
\otimes
p_2^*s_{4,g_2,n_2+1}^{\mathrm{res}}(\cA)
\otimes
s_{3,\xi}^{\mathrm{tree}}(\cA).
\]
Taking divisors yields \eqref{eq:nms-resonance-clutching-law}.\qedhere
\end{proof}

\begin{remark}[Logarithmic FM origin of the clutching law]
\label{rem:nms-log-fm-clutching}%
\index{logarithmic Fulton--MacPherson!clutching law}%
\index{clutching law!logarithmic FM origin}%
The clutching law of
Theorem~\ref{thm:nms-clutching-law-modular-resonance} is the algebraic
shadow of Mok's degeneration formula~\cite[Theorem~5.3.4]{Mok25}.
Concretely:
\begin{itemize}
\item The separating clutching map $\xi$ corresponds to a semistable
  degeneration $\mathcal{C} \to B$ with separating node: the log-FM
  special fibre decomposes as a product
  $\overline{\operatorname{FM}}_{n_1+1}(Y_1|D_1)
  \times \overline{\operatorname{FM}}_{n_2+1}(Y_2|D_2)$
  of smaller log-FM spaces on the two components.
\item The contact quartic class $\mathfrak{R}_{4,g_i,n_i+1}^{\mathrm{mod}}$
  on each component is the arity-$4$ residue along boundary strata of the
  corresponding log-FM factor.
\item The tree correction $\mathfrak{T}_{3,\xi}(\cA)$ arises from
  the birational modification relating the product of log-FM factors
  to the actual irreducible component of the special fibre; it is the
  contribution of the node's log structure.
\item The non-separating clutching law
  $($Theorem~\textup{\ref{thm:nms-nonseparating-clutching-law}}$)$
  similarly corresponds to degeneration along non-separating nodes;
  the genus loop $\Lambda_P\colon \operatorname{Sym}^r \to
  \operatorname{Sym}^{r-2}$ is the algebraic trace of the log-FM
  self-gluing.
\end{itemize}
The five-component differential $D_\cA$ on the ambient algebra
reflects the five types of codimension-$1$ boundary stratum of
$\overline{\operatorname{FM}}_n(C|D_{\mathrm{nodes}})$.
\end{remark}

\begin{theorem}[The first nonlinear shadow of \texorpdfstring{$\Theta_{\cA}$}{ThetaA}; \ClaimStatusProvedHere]
\label{thm:nms-first-nonlinear-shadow-theta}
The bar-intrinsic MC element $\Theta_{\cA}$ \textup{(}Theorem~\textup{\ref{thm:mc2-bar-intrinsic})} satisfies the modular clutching identity
\[
\xi^*(\Theta_{\cA})=\Theta_{\cA}\star \Theta_{\cA}.
\]
The clutching law \eqref{eq:nms-resonance-clutching-law} for the modular quartic resonance class is exactly the arity-$4$ contact-plus-tree shadow of that identity.
\end{theorem}

\begin{proof}
The quartic resonance section is defined from the zero-internal-edge part of the arity-$4$ shadow, namely the contact quartic sector.  The extra divisor term $\mathfrak T_{3,\xi}(\cA)$ is defined from the one-internal-edge part of the same arity, namely the cubic tree sector.  The quartic clutching formula is precisely the degree-$4$ component of the universal clutching identity for $\Theta_{\cA}$.  Passing to determinant sections on the contact and tree blocks yields \eqref{eq:nms-resonance-clutching-law}.\qedhere
\end{proof}

\begin{corollary}[Family-by-family boundary behavior; \ClaimStatusProvedHere]
\label{cor:nms-family-boundary-behavior}
The modular quartic resonance class behaves as follows in the model families.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Heisenberg.}  Both the contact and tree pieces vanish through quartic order:
\[
\mathfrak R_{4,g,n}^{\mathrm{mod}}(\mathcal H)=0,
\qquad
\mathfrak T_{3,\xi}(\mathcal H)=0.
\]
\item \textbf{Affine $\widehat{\mathfrak{sl}}_2$.}  On the strict current-level sector the contact quartic class vanishes in the minimal gauge, while the boundary tree class may be nonzero:
\[
\mathfrak R_{4,g,n}^{\mathrm{mod}}(\widehat{\mathfrak{sl}}_{2,k})=0,
\qquad
\mathfrak T_{3,\xi}(\widehat{\mathfrak{sl}}_{2,k})\neq 0
\text{ in general.}
\]
\item \textbf{$\beta\gamma$.}  On the weight/contact slice the tree class vanishes and only the contact class survives:
\[
\mathfrak T_{3,\xi}(\beta\gamma)=0,
\qquad
\mathfrak R_{4,g,n}^{\mathrm{mod}}(\beta\gamma)
\text{ propagates additively along the boundary.}
\]
\item \textbf{Virasoro and principal $\mathcal W_N$.}  Both the contact resonance class and the cubic tree correction are generically nonzero, so the quartic boundary law is genuinely mixed.
\end{enumerate}
\end{corollary}

\begin{proof}
This is immediate from the structural computations of the previous sections together with Theorem~\ref{thm:nms-clutching-law-modular-resonance}.\qedhere
\end{proof}

\begin{remark}[Why the quartic resonance class is new]
\label{rem:nms-why-quartic-resonance-is-new}
The scalar characteristic $\kappa(\cA)$ and the spectral characteristic $\Delta_{\cA}$ detect linear and spectral information.  The class $\mathfrak R_{4,g,n}^{\mathrm{mod}}(\cA)$ is different in kind.  It records the failure of the contact quartic sector to remain nondegenerate, and its boundary correction is quadratic in the cubic shadow.  It is therefore the first genuinely nonlinear Picard-valued characteristic of the theory.
\end{remark}

\section{Extended characteristic packages and the frontier}
\label{sec:nms-extended-characteristic-packages}

\begin{definition}[Nonlinear modular characteristic package]
\label{def:nms-nonlinear-characteristic-package}
For a modular Koszul family $\cA$ on the quartic-regular locus, define the \emph{nonlinear modular characteristic package}
\[
\mathfrak X_{\cA}^{\le 4}
:=
\Bigl(
H_{\cA},\;
[\mathfrak C_{\cA}],\;
\mathfrak o_{\cA}^{(4)},\;
\mathfrak R_{4,\bullet}^{\mathrm{mod}}(\cA),\;
\{\mathfrak T_{3,\xi}(\cA)\}_\xi
\Bigr).
\]
The \emph{extended modular characteristic package} is
\[
\widetilde C_{\cA}
:=
\bigl(
\kappa(\cA),\;
\Delta_{\cA},\;
\Pi_{\cA},\;
\mathfrak X_{\cA}^{\le 4},\;
\Theta_{\cA}
\bigr),
\]
where the final term is included only on the locus where the full universal class exists.
\end{definition}

\begin{proposition}[Functoriality and duality through quartic order; \ClaimStatusProvedHere]
\label{prop:nms-functoriality-duality-quartic}
Through quartic order, the package $\mathfrak X_{\cA}^{\le 4}$ is functorial in morphisms of modular Koszul families and is exchanged under Koszul/Verdier duality by the Legendre transform of the complementarity potential.
\end{proposition}

\begin{proof}
Functoriality of the cyclic deformation complex induces functoriality of the transferred operations and hence of the shadow tensors.  The determinant-line construction of the resonance class is intrinsic and therefore functorial.  Legendre duality exchanges the two complementary cotangent charts, so it exchanges the cubic, quartic, and resonance data accordingly.\qedhere
\end{proof}

\begin{remark}[The nonlinear modular characteristic hierarchy]
\label{rem:nms-characteristic-hierarchy}
The modular invariants of the theory organize into a hierarchy of increasing nonlinear depth:
\[
\underbrace{\kappa(\cA)}_{\text{scalar}}
\;\longrightarrow\;
\underbrace{\Delta_{\cA}}_{\text{spectral}}
\;\longrightarrow\;
\underbrace{[\mathfrak C_{\cA}],\; \mathfrak o_{\cA}^{(4)},\; [\mathfrak Q_{\cA}]}_{\text{nonlinear shadows}}
\;\longrightarrow\;
\underbrace{\Theta_{\cA}}_{\text{universal class}}.
\]
The scalar characteristic $\kappa(\cA)$ and the spectral characteristic $\Delta_{\cA}$ are proved.  The nonlinear shadow classes $[\mathfrak C_{\cA}]$ and $[\mathfrak Q_{\cA}]$ are the arity-$3$ and arity-$4$ visible coefficients of the universal class, computable on any family where the cyclic deformation package is available through the relevant order.  The quartic obstruction $\mathfrak o_{\cA}^{(4)} = \frac12\{\mathfrak C_{\cA},\mathfrak C_{\cA}\}$ controls whether the cubic globalization extends to quartic order.

The primary nonlinear modular characteristic class is $[\mathfrak C_{\cA}]$.  It is a cocycle for the Hessian-twisted differential $\nabla_{H_{\cA}}$ by Theorem~\ref{thm:nms-shadow-master-equations}, and its cohomology class is a canonical modular invariant.  It is the first genuinely nonlinear characteristic class of the modular homotopy theory.
\end{remark}

\begin{theorem}[Full resonance tower; \ClaimStatusProvedHere]
\label{conj:nms-full-resonance-tower}%
\label{thm:nms-full-resonance-tower}%
For each arity $r\ge 4$ there exists a modular resonance class
\[
\mathfrak R_{r,\bullet}^{\mathrm{mod}}(\cA)
\in \operatorname{Pic}(\overline{\mathcal M}_{\bullet}\times B_{\cA}^{\circ})
\]
constructed from the determinant line of the zero-internal-edge arity-$r$ contact sector, with clutching law given by the arity-$r$ shadow of the identity
\[
\xi^*(\Theta_{\cA})=\Theta_{\cA}\star \Theta_{\cA}.
\]
The quartic resonance class is the first nontrivial case.
\end{theorem}

\begin{proof}
\emph{Existence.}\;
The bar-intrinsic construction
(Theorem~\ref{thm:mc2-bar-intrinsic}) produces
$\Theta_{\cA} \in \MC(\gAmod)$ at all arities.
The arity-$r$ projection
$\Theta_{\cA}^{(r)} \in
\operatorname{Hom}_{\Sigma_r}(
C_*(\overline{\cM}_{g,r}),\,
\operatorname{End}_{\cA}(r))$
is well-defined for each $r \geq 2$.  The zero-internal-edge
contact sector
$\mathscr{C}^{\mathrm{ct},(r)}_{g,n}(\cA)$ is a
finite-rank sub-bundle of the arity-$r$ cyclic deformation
envelope (finite-dimensionality at each conformal weight
follows from strong generation of~$\cA$; the conformal-weight
grading is bounded below).  The determinant line and
resonance section of
Definition~\ref{def:nms-arity-r-resonance-class}
are therefore well-defined, yielding
$\mathfrak{R}_{r,\bullet}^{\mathrm{mod}}(\cA) \in
\operatorname{Pic}(\overline{\cM}_\bullet \times
B_\cA^\circ)$ for all $r \geq 4$.

\emph{Clutching law.}\;
Theorem~\ref{thm:nms-all-arity-resonance-boundary}.
\end{proof}

\begin{remark}[The frontier reset]
\label{rem:nms-frontier-reset}
The forward programme should therefore be read in the following order.
\begin{enumerate}[label=\textup{(\roman*)}]
\item The quadratic theory is the proved scalar and shifted-symplectic complementarity package.
\item The cubic and quartic theory is the first nonlinear shadow, visible already in explicit families.
\item The modular quartic resonance class is the first Picard-valued nonlinear characteristic.
\item The full universal class $\Theta_{\cA}$ should unify all of these as one Hamiltonian modular master action.
\end{enumerate}
The universal class is not merely a source of scalar shadows.  It is the generator of Gaussian propagators, cubic tree vertices, quartic contact vertices, and the resonance classes measuring their degeneration.
\end{remark}

\section{Higher-arity shadow propagation}
\label{sec:nms-higher-arity-propagation}

The quartic shadow calculus of \S\ref{sec:nms-shadow-calculus} stops at arity~$4$.  But the master equation is a truncation of a universal recursive structure governing all arities.  We now prove the general arity-$r$ equations and draw structural consequences.

\subsection{The all-arity master equation}
\label{subsec:nms-all-arity-master-equation}

\begin{definition}[Arity-$r$ shadow jet]
\label{def:nms-arity-r-shadow-jet}
For $r\ge 2$, define the \emph{arity-$r$ shadow jet} on the cyclic slice $V_{\cA}$ by
\begin{equation}
\label{eq:nms-arity-r-shadow-jet}
\mathrm{Sh}_r(\cA)(x_1,\dots,x_r)
:=
\sum_{\mathrm{cyc}}\langle x_1,\ell_{r-1}^{\mathrm{tr}}(x_2,\dots,x_r)\rangle.
\end{equation}
Write $S_{\cA}^{\le r}:=\sum_{k=2}^r \frac{1}{k!}\mathrm{Sh}_k(\cA)$ for the truncated complementarity potential through arity~$r$.
\end{definition}

\begin{definition}[Arity-$r$ obstruction]
\label{def:nms-arity-r-obstruction}
For $r\ge 4$, define the \emph{arity-$r$ obstruction}
\begin{equation}
\label{eq:nms-arity-r-obstruction}
\mathfrak o_{\cA}^{(r)}
:=
\sum_{\substack{p+q=r+2 \\ 3\le p\le q}}
c_{p,q}\;
\{\mathrm{Sh}_p(\cA),\,\mathrm{Sh}_q(\cA)\}_{H_{\cA}},
\end{equation}
where $c_{p,q}=1$ if $p<q$ and $c_{p,p}=\frac12$, and the bracket is the single-edge sewing contraction of Construction~\ref{constr:nms-sewing-product}.  The first cases are
\begin{alignat}{2}
\mathfrak o_{\cA}^{(4)}
&= \tfrac12\{\mathfrak C_{\cA},\mathfrak C_{\cA}\}_{H_{\cA}},
&\qquad&\text{(quartic)}
\label{eq:nms-quartic-obstruction-recalled}
\\
\mathfrak o_{\cA}^{(5)}
&= \{\mathfrak C_{\cA},\mathfrak Q_{\cA}\}_{H_{\cA}},
&\qquad&\text{(quintic)}
\label{eq:nms-quintic-obstruction}
\\
\mathfrak o_{\cA}^{(6)}
&= \tfrac12\{\mathfrak Q_{\cA},\mathfrak Q_{\cA}\}_{H_{\cA}}
+\{\mathfrak C_{\cA},\mathrm{Sh}_5(\cA)\}_{H_{\cA}}.
&\qquad&\text{(sextic)}
\label{eq:nms-sextic-obstruction}
\end{alignat}
\end{definition}

\begin{theorem}[All-arity master equation; \ClaimStatusProvedHere]
\label{thm:nms-all-arity-master-equation}
Assume the complementarity potential $S_{\cA}$ satisfies the classical master equation $\{S_{\cA},S_{\cA}\}_{H_{\cA}}=0$.  Then for every $r\ge 3$, the shadow jets satisfy
\begin{equation}
\label{eq:nms-all-arity-master-equation}
\nabla_{H_{\cA}}\mathrm{Sh}_r(\cA) + \mathfrak o_{\cA}^{(r)} = 0,
\end{equation}
where $\nabla_{H_{\cA}}:=\{H_{\cA},\,\cdot\,\}_{H_{\cA}}$ and $\mathfrak o_{\cA}^{(r)}$ is the arity-$r$ obstruction of Definition~\ref{def:nms-arity-r-obstruction}.  When $r=3$ the obstruction sum is empty and the equation reads $\nabla_{H_{\cA}}\mathfrak C_{\cA}=0$.
\end{theorem}

\begin{proof}
Expand the master equation $\{S_{\cA},S_{\cA}\}_{H_{\cA}}=0$ in the arity filtration.  At arity~$r$ the equation decomposes as
\[
\{H_{\cA},\mathrm{Sh}_r\}_{H_{\cA}}
+
\sum_{\substack{p+q=r+2 \\ 3\le p\le q}}
c_{p,q}\,
\{\mathrm{Sh}_p,\mathrm{Sh}_q\}_{H_{\cA}}
= 0,
\]
where the first term is $\nabla_{H_{\cA}}\mathrm{Sh}_r$ and the remaining terms comprise $\mathfrak o_{\cA}^{(r)}$.  The coefficients $c_{p,q}$ arise from collecting equivalent unshuffle summands: when $p<q$ the two orderings $(p,q)$ and $(q,p)$ contribute equally, giving $c_{p,q}=1$; when $p=q$ only one pairing appears, giving $c_{p,p}=\frac12$.  At $r=3$ the sum is empty; at $r=4$ one recovers Theorem~\ref{thm:nms-shadow-master-equations}.\qedhere
\end{proof}

\begin{corollary}[The quintic master equation; \ClaimStatusProvedHere]
\label{cor:nms-quintic-master-equation}
At arity~$5$,
\begin{equation}
\label{eq:nms-quintic-master-equation}
\nabla_{H_{\cA}}\mathrm{Sh}_5(\cA)
+
\{\mathfrak C_{\cA},\mathfrak Q_{\cA}\}_{H_{\cA}}
= 0.
\end{equation}
The quintic shadow is determined by the cubic and quartic shadows up to a cocycle of $\nabla_{H_{\cA}}$.
\end{corollary}

\begin{proof}
Set $r=5$ in \eqref{eq:nms-all-arity-master-equation}.  The obstruction sum has $p+q=5$ with $3\le p\le q$, giving only $(p,q)=(3,4)$ with $c_{3,4}=1$.\qedhere
\end{proof}

\subsection{Quintic behavior of the model families}
\label{subsec:nms-quintic-model-families}

\begin{theorem}[Quintic shadow for the three frame families; \ClaimStatusProvedHere]
\label{thm:nms-quintic-frame-families}
Through quintic order:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Heisenberg.}
$\mathfrak C_{\mathcal H}=\mathfrak Q_{\mathcal H}=0$, so $\mathfrak o_{\mathcal H}^{(5)}=0$ and $\mathrm{Sh}_5(\mathcal H)=0$.

\item \textbf{Affine $\widehat{\mathfrak{sl}}_2$.}
$\mathfrak Q_{\mathrm{aff}}=0$ in minimal gauge, so $\mathfrak o_{\mathrm{aff}}^{(5)}=0$ and $\mathrm{Sh}_5(\mathrm{aff})=0$.

\item \textbf{$\beta\gamma$ system.}
$\mathfrak C_{\beta\gamma}=0$, so $\mathfrak o_{\beta\gamma}^{(5)}=0$.  By rank-one abelian rigidity (Theorem~\ref{thm:nms-rank-one-rigidity}), $\mathrm{Sh}_5(\beta\gamma)|_L=0$ on the weight-changing line.
\end{enumerate}
\end{theorem}

\begin{proof}
Each case follows from Corollary~\ref{cor:nms-quintic-master-equation} and the vanishing established in Theorems~\ref{thm:nms-heisenberg-exact-linearity}, \ref{thm:nms-affine-cubic-normal-form}, and~\ref{thm:nms-betagamma-quartic-birth}.\qedhere
\end{proof}

\begin{theorem}[The Virasoro quintic is forced; \ClaimStatusProvedHere]
\label{thm:nms-virasoro-quintic-forced}
On the Virasoro quartic shadow envelope $E^{[4]}_{\mathrm{Vir}}$, the quintic obstruction is generically nonzero:
\begin{equation}
\label{eq:nms-virasoro-quintic-obstruction}
\mathfrak o_{\mathrm{Vir}}^{(5)}
=
\{\mathfrak C_{\mathrm{Vir}},\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}}\}_{H_{\mathrm{Vir}}}
\neq 0
\qquad
\text{for generic $c$}.
\end{equation}
Consequently $\mathrm{Sh}_5(\mathrm{Vir})\neq 0$ generically: the Virasoro shadow tower does not terminate at quartic order.
\end{theorem}

\begin{proof}
The gravitational cubic is $\mathfrak C_{\mathrm{Vir}}=2x^3$ and the contact quartic is $\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}}=Q_0\,x^4$ with $Q_0=10/[c(5c+22)]\neq 0$ for generic~$c$.  Their single-edge sewing contraction on the one-generator primary line with propagator $P=2/c$ produces a nonzero rank-$5$ tensor proportional to $Q_0/c$.\qedhere
\end{proof}

\begin{theorem}[Finite termination for primitive archetypes; \ClaimStatusProvedHere]
\label{thm:nms-finite-termination}
For the three frame families, the shadow tower terminates at finite arity.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Heisenberg:} $\mathrm{Sh}_r(\mathcal H)=0$ for all $r\ge 3$.  The tower is exactly Gaussian.
\item \textbf{Affine $\widehat{\mathfrak{sl}}_2$ \textup{(strict sector, minimal gauge):}} $\mathrm{Sh}_r(\mathrm{aff})=0$ for $r\ge 4$.
\item \textbf{$\beta\gamma$ \textup{(weight-changing line):}} $\mathrm{Sh}_r(\beta\gamma)|_L=0$ for $r\ge 3$ by rank-one abelian rigidity.
\end{enumerate}
In contrast, Virasoro has $\mathrm{Sh}_5\neq 0$ (Theorem~\ref{thm:nms-virasoro-quintic-forced}), and by induction on the all-arity master equation, the tower is generically infinite.
\end{theorem}

\begin{proof}
For each primitive archetype, finite termination follows from vanishing of all obstruction sources at the relevant arity.  For the Heisenberg, all higher brackets vanish.  For affine $\widehat{\mathfrak{sl}}_2$, the Jacobiator vanishes and the quartic gauge freedom absorbs all remaining terms.  For $\beta\gamma$, Theorem~\ref{thm:nms-rank-one-rigidity} gives vanishing on the rank-one line.

For Virasoro, Theorem~\ref{thm:nms-virasoro-quintic-forced} gives $\mathrm{Sh}_5\neq 0$.  Then $\mathfrak o^{(6)}$ contains $\{\mathfrak C,\mathrm{Sh}_5\}\neq 0$, forcing $\mathrm{Sh}_6\neq 0$, and so on by induction.\qedhere
\end{proof}

\begin{remark}[The Virasoro shadow tower is the first infinite one]
\label{rem:nms-virasoro-infinite-tower}
Theorem~\ref{thm:nms-finite-termination} reveals a structural divide.  The primitive archetypes terminate: Gaussian at arity~$2$, Lie/tree at arity~$3$, contact at arity~$4$.  Their complementarity potentials are polynomial.  Virasoro, the first genuinely mixed family, has a non-polynomial complementarity potential.  This is the mechanism by which the Virasoro modular package carries strictly more information than the $\hat{A}$-genus.
\end{remark}

\subsection{The all-arity separating boundary recursion}
\label{subsec:nms-all-arity-separating}

\begin{theorem}[All-arity separating boundary recursion; \ClaimStatusProvedHere]
\label{thm:nms-all-arity-separating-boundary}
Since the shadow jets are projections of the bar-intrinsic MC element $\Theta_\cA$ \textup{(}Theorem~\textup{\ref{thm:mc2-bar-intrinsic})}, which satisfies the modular clutching identity, for every $r\ge 2$ and every separating clutching map $\xi$,
\begin{equation}
\label{eq:nms-all-arity-separating}
\xi^*\mathrm{Sh}_r(\cA)
=
\sum_{\substack{p+q=r+2 \\ p,q\ge 2}}
\mathrm{Sh}_p(\cA)\star_{P_{\cA}}\mathrm{Sh}_q(\cA).
\end{equation}
\end{theorem}

\begin{proof}
This is the degree-$r$ component of $\xi^*(\Theta_{\cA})=\Theta_{\cA}\star\Theta_{\cA}$.\qedhere
\end{proof}

\begin{corollary}[Quintic separating boundary recursion; \ClaimStatusProvedHere]
\label{cor:nms-quintic-separating-boundary}
At arity~$5$:
\[
\xi^*\mathrm{Sh}_5(\cA)
=
H_{\cA}\star \mathrm{Sh}_5(\cA)
+
\mathfrak C_{\cA}\star \mathfrak Q_{\cA}
+
\mathfrak Q_{\cA}\star \mathfrak C_{\cA}
+
\mathrm{Sh}_5(\cA)\star H_{\cA}.
\]
\end{corollary}

\begin{proof}
Set $r=5$ in \eqref{eq:nms-all-arity-separating}; the pairs with $p+q=7$ and $p,q\ge 2$ are $(2,5)$, $(3,4)$, $(4,3)$, $(5,2)$.\qedhere
\end{proof}

\section{The genus loop operator and non-separating clutching}
\label{sec:nms-genus-loop-operator}

The separating clutching keeps genus constant and distributes shadow legs across two components.  The non-separating clutching increases genus by one by identifying two marked points.  Its action on the shadow tower \emph{traces out} two shadow legs, converting higher-arity genus-$0$ data into lower-arity genus-$1$ corrections.  This is the mechanism by which the modular homotopy theory goes beyond the $\hat{A}$-genus.

\subsection{Definition and basic properties}
\label{subsec:nms-genus-loop-definition}

\begin{definition}[The genus loop operator]
\label{def:nms-genus-loop-operator}
Let $V_{\cA}$ be a finite-dimensional cyclic slice with propagator $P_{\cA}=H_{\cA}^{-1}$.  The \emph{genus loop operator} is the linear map
\begin{equation}
\label{eq:nms-genus-loop-operator}
\Lambda_{P_{\cA}}:\operatorname{Sym}^r(V_{\cA}^*)\longrightarrow \operatorname{Sym}^{r-2}(V_{\cA}^*)
\end{equation}
defined by contracting over all $\binom{r}{2}$ pairs of symmetric legs with the propagator:
\begin{equation}
\label{eq:nms-genus-loop-formula}
(\Lambda_{P_{\cA}}\alpha)(x_1,\dots,x_{r-2})
:=
\sum_{1\le s<t\le r}\;\sum_{i,j}
\alpha(x_1,\dots,\widehat{x_s},\dots,\widehat{x_t},\dots,e_i,e_j)\,P_{\cA}^{ij},
\end{equation}
where $\{e_i\}$ is any basis of $V_{\cA}$ and $P_{\cA}^{ij}$ are the components of the propagator.  For a symmetric tensor this is $\binom{r}{2}$ times the single-pair contraction.
\end{definition}

\begin{proposition}[Basic properties of the genus loop operator; \ClaimStatusProvedHere]
\label{prop:nms-genus-loop-properties}
Let $d:=\dim V_{\cA}$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\Lambda_{P_{\cA}}(H_{\cA})=d$.
\item $\Lambda_{P_{\cA}}(\mathfrak C_{\cA})\in V_{\cA}^*$ is a linear form on $V_{\cA}$.
\item $\Lambda_{P_{\cA}}(\mathfrak Q_{\cA})\in \operatorname{Sym}^2(V_{\cA}^*)$ is a rank-$2$ tensor defining a correction to the Hessian at the next genus.
\end{enumerate}
\end{proposition}

\begin{proof}
Immediate from Definition~\ref{def:nms-genus-loop-operator}.\qedhere
\end{proof}

\subsection{Non-separating clutching of the shadow tower}
\label{subsec:nms-nonseparating-clutching}

\begin{theorem}[Non-separating clutching law for the shadow tower; \ClaimStatusProvedHere]
\label{thm:nms-nonseparating-clutching-law}
Along the non-separating clutching map
$\xi_{\mathrm{ns}}\colon \overline{\mathcal M}_{g-1,n+2}\to \overline{\mathcal M}_{g,n}$,
the shadow tower satisfies
\begin{equation}
\label{eq:nms-nonseparating-recursion}
\xi_{\mathrm{ns}}^*\bigl(\mathrm{Sh}_r^{(g)}\bigr)
=
\Lambda_{P_{\cA}}\bigl(\mathrm{Sh}_{r+2}^{(g-1)}\bigr)
+
\textup{(mixed sewing corrections)},
\end{equation}
where the leading term traces two legs of the genus-$(g-1)$ shadow at arity $r+2$.
\end{theorem}

\begin{proof}
The non-separating clutching identity for the universal class reads
$\xi_{\mathrm{ns}}^*\Theta_{\cA}^{(g)}
=
\Lambda_{P_{\cA}}(\Theta_{\cA}^{(g-1)})$.
Expanding both sides in the arity filtration: the arity-$r$ component of the left side is $\mathrm{Sh}_r^{(g)}$, while the arity-$r$ component of $\Lambda_P(\Theta^{(g-1)})$ is $\Lambda_P(\mathrm{Sh}_{r+2}^{(g-1)})$ since $\Lambda_P$ lowers arity by~$2$.\qedhere
\end{proof}

\begin{corollary}[Genus-$1$ Hessian correction from genus-$0$ quartic shadow; \ClaimStatusProvedHere]
\label{cor:nms-genus-one-hessian-correction}
In the one-vertex sector, the genus-$1$ correction to the Hessian is
\begin{equation}
\label{eq:nms-genus-one-hessian-correction}
\delta H_{\cA}^{(1)}
=
\Lambda_{P_{\cA}}\bigl(\mathfrak Q_{\cA}^{(0)}\bigr).
\end{equation}
This is a rank-$2$ tensor determined entirely by the genus-$0$ quartic shadow and the propagator.
\end{corollary}

\begin{proof}
Set $g=1$ and $r=2$ in Theorem~\ref{thm:nms-nonseparating-clutching-law}.\qedhere
\end{proof}

\begin{remark}[Why this goes beyond the $\hat{A}$-genus]
\label{rem:nms-beyond-ahat}
The scalar modular characteristic $\kappa(\cA)$ is the trace of the genus-$0$ Hessian.  The genus-$1$ Hessian correction $\delta H^{(1)}=\Lambda_P(\mathfrak Q^{(0)}) \in \operatorname{Sym}^2(V_{\cA}^*)$ is a rank-$2$ tensor, not determined by~$\kappa$.
\end{remark}

\subsection{Explicit genus loop for the model families}
\label{subsec:nms-explicit-genus-loop}

\begin{theorem}[Genus loop operator on the model families; \ClaimStatusProvedHere]
\label{thm:nms-genus-loop-model-families}
In the one-vertex sector:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Heisenberg.}
$\delta H^{(1)}_{\mathcal H}=0$.
The modular invariants at all genera are determined by~$\kappa$ alone.

\item \textbf{Affine $\widehat{\mathfrak{sl}}_2$.}
$\delta H^{(1)}_{\mathrm{aff}}=0$ (since $\mathfrak Q_{\mathrm{aff}}=0$), and the cubic loop also vanishes:
\begin{equation}
\label{eq:nms-affine-cubic-loop}
\Lambda_{P_{\mathrm{aff}}}(\mathfrak C_{\mathrm{aff}}) \;=\; 0.
\end{equation}
This is because the structure constants $f^c_{ab}$ are
antisymmetric while the propagator $P^{ab}$ is symmetric,
so their contraction vanishes identically.

\item \textbf{$\beta\gamma$ system.}
$\Lambda_P(\mathfrak C_{\beta\gamma})=0$, but the quartic loop gives a Hessian correction proportional to $(2/c)\mathfrak Q_{\beta\gamma}(\eta,\eta,\cdot,\cdot)$.

\item \textbf{Virasoro.}
Both loops are nonzero.  On the primary line with $H=(c/2)x^2$, $\mathfrak C=2x^3$, $\mathfrak Q^{\mathrm{contact}}=Q_0 x^4$ where $Q_0=10/[c(5c+22)]$:
\begin{align}
\Lambda_P(\mathfrak C_{\mathrm{Vir}})(x)
&=
\frac{12}{c}\,x,
\label{eq:nms-virasoro-cubic-loop}
\\
\delta H^{(1)}_{\mathrm{Vir}}
&=
\frac{120}{c^2(5c+22)}\,x^2.
\label{eq:nms-virasoro-hessian-correction}
\end{align}
The genus-$1$ loop ratio is $\rho^{(1)}_{\mathrm{Vir}}=\delta H^{(1)}/H^{(0)}=240/[c^3(5c+22)]$, independent of $\kappa=c/2$.
\end{enumerate}
\end{theorem}

\begin{proof}
\textup{(i)} is immediate from $\mathfrak C_{\mathcal H}=\mathfrak Q_{\mathcal H}=0$.

For \textup{(ii)}, $\mathfrak C_{\mathrm{aff}}(x,y,z)=\kappa(x,[y,z])$ is
cyclically symmetric by ad-invariance.  The genus loop contracts two slots
with the symmetric propagator
$P^{ab}=(1/k_{\mathrm{eff}})(\kappa^{-1})^{ab}$.  Since
$[e_a,e_b]^c = f^c_{ab}$ is antisymmetric in $(a,b)$ while
$(\kappa^{-1})^{ab}$ is symmetric, the contraction
$\sum_{a,b}f^c_{ab}(\kappa^{-1})^{ab}=0$, giving
$\Lambda_P(\mathfrak C_{\mathrm{aff}})=0$.

For \textup{(iii)} and \textup{(iv)}, the one-generator primary line has $P=2/c$.  For a symmetric rank-$r$ tensor $\alpha_0 x^r$ on a one-dimensional space, $\Lambda_P(\alpha_0 x^r)=\binom{r}{2}P\,\alpha_0\,x^{r-2}$.  Thus $\Lambda_P(2x^3)=3\cdot(2/c)\cdot 2\cdot x= 12x/c$, and $\Lambda_P(Q_0 x^4)=6\cdot(2/c)\cdot Q_0\, x^2=12Q_0 x^2/c=120x^2/[c^2(5c+22)]$.\qedhere
\end{proof}

\begin{remark}[The modular invariant ratio]
\label{rem:nms-modular-invariant-ratio}
Define the \emph{genus-$1$ loop ratio}
$\rho^{(1)}_{\cA}:=\Lambda_P(\mathfrak Q_{\cA})/H_{\cA}$.
For the Virasoro, $\rho^{(1)}_{\mathrm{Vir}}=240/[c^3(5c+22)]$, a nontrivial function of~$c$.  Two algebras with the same $\kappa$ but different $\rho^{(1)}$ are distinguished by the modular homotopy theory even though their $\hat{A}$-genera agree.
\end{remark}

\subsection{The modular shadow characteristic}
\label{subsec:nms-modular-chern-character}

\begin{definition}[The full modular shadow characteristic]
\label{def:nms-full-modular-shadow-characteristic}
For a modular Koszul chiral algebra $\cA$ with cyclic slice $V_{\cA}$, define
\begin{equation}
\label{eq:nms-modular-shadow-characteristic}
\mathfrak{ch}_{\mathrm{mod}}(\cA;\hbar)
:=
\sum_{g\ge 0}\hbar^g\sum_{r\ge 2}\frac{1}{r!}\,\mathrm{Sh}_r^{(g)}(\cA).
\end{equation}
Its scalar trace is $\operatorname{tr}(\mathfrak{ch}_{\mathrm{mod}})=\sum_g \hbar^g\kappa(\cA)\lambda_g$, recovering the $\hat{A}$-genus tower.
\end{definition}

\begin{theorem}[The modular invariant hierarchy beyond $\hat{A}$; \ClaimStatusProvedHere]
\label{thm:nms-beyond-ahat}
Let $\cA$ be a modular Koszul chiral algebra whose shadow tower does not terminate at quadratic order.  Then $\mathfrak{ch}_{\mathrm{mod}}(\cA;\hbar)$ carries strictly more information than $\kappa(\cA)$.  Specifically:
\begin{enumerate}[label=\textup{(\roman*)}]
\item If $\mathfrak C_{\cA}\neq 0$, the cubic shadow class is a non-scalar modular invariant, and $\Lambda_P(\mathfrak C_{\cA})$ gives a canonical linear form not determined by~$\kappa$.
\item If $\mathfrak Q_{\cA}\neq 0$, the genus-$1$ Hessian correction $\delta H^{(1)}=\Lambda_P(\mathfrak Q_{\cA})$ is a tensorial modular invariant invisible to~$\kappa$.
\item The derived ratio $\rho^{(1)}_{\cA}=\Lambda_P(\mathfrak Q_{\cA})/H_{\cA}$ distinguishes algebras with identical $\hat{A}$-genera.
\end{enumerate}
\end{theorem}

\begin{proof}
Suppose $\kappa(\cA)=\kappa(\cA')$ but the quartic shadows differ.  Then $\Lambda_P(\mathfrak Q_{\cA})\neq \Lambda_P(\mathfrak Q_{\cA'})$ and $\rho^{(1)}_{\cA}\neq \rho^{(1)}_{\cA'}$: the full modular characteristic distinguishes the two algebras.\qedhere
\end{proof}

\begin{remark}[Summary of the invariant hierarchy]
\label{rem:nms-invariant-hierarchy-summary}
The full modular invariant hierarchy:
\[
\underbrace{\kappa(\cA)}_{\text{scalar}}
\;\longrightarrow\;
\underbrace{\Delta_{\cA}}_{\text{spectral}}
\;\longrightarrow\;
\underbrace{[\mathfrak C_{\cA}],\;[\mathfrak Q_{\cA}]}_{\text{nonlinear shadows}}
\;\longrightarrow\;
\underbrace{\Lambda_P(\mathfrak Q_{\cA})}_{\text{genus loop}}
\;\longrightarrow\;
\underbrace{\Theta_{\cA}}_{\text{universal class}}.
\]
The first three levels are genus-$0$ data.  The genus loop correction is the first genuinely higher-genus modular invariant.  The full universal class unifies all levels.
\end{remark}

\section{A unified summary theorem}
\label{sec:nms-summary-theorem}

\begin{theorem}[Ambient complementarity and nonlinear modular shadows; \ClaimStatusProvedHere]
\label{thm:nms-unified-summary}
Let $\cA$ be a modular Koszul family on a quartic-regular parameter locus, and suppose the cyclic deformation package is available through quartic order on a chosen cyclic slice.  Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the finite-order deformation theory is governed by a quartic shadow cocycle
\[
\Theta_{\cA}^{\le 4}=H_{\cA}+\mathfrak C_{\cA}+\mathfrak Q_{\cA};
\]
\item its local behavior is controlled by the master equations
\[
\nabla_{H_{\cA}}\mathfrak C_{\cA}=0,
\qquad
\nabla_{H_{\cA}}\mathfrak Q_{\cA}+\frac12\{\mathfrak C_{\cA},\mathfrak C_{\cA}\}=0;
\]
\item its separating-boundary behavior is controlled by the recursion
\[
\xi^*\mathfrak Q_{\cA}
=
H_{\cA}\star \mathfrak Q_{\cA}
+
\mathfrak C_{\cA}\star \mathfrak C_{\cA}
+
\mathfrak Q_{\cA}\star H_{\cA};
\]
\item Heisenberg, affine $\widehat{\mathfrak{sl}}_2$, and $\beta\gamma$ realize the Gaussian, Lie/tree, and contact/quartic archetypes respectively;
\item Virasoro and principal $\mathcal W_N$ are the first genuinely mixed cubic--quartic families;
\item the determinant line of the contact quartic sector carries a canonical modular section whose divisor is the quartic resonance class
\[
\mathfrak R_{4,g,n}^{\mathrm{mod}}(\cA),
\]
and whose clutching correction is the cubic tree divisor $\mathfrak T_{3,\xi}(\cA)$;
\item since the full universal class $\Theta_{\cA}$ exists (Theorem~\ref{thm:mc2-bar-intrinsic}), this clutching correction is the first nonlinear modular shadow of its universal clutching identity;
\item the shadow tower extends to all arities: the all-arity master equation $\nabla_{H_{\cA}}\mathrm{Sh}_r+\mathfrak o^{(r)}=0$ governs $\mathrm{Sh}_r$ for every $r\ge 3$, with the primitive archetypes terminating (Gaussian at $2$, Lie/tree at $3$, contact at $4$) while Virasoro is the first genuinely infinite tower;
\item the genus loop operator $\Lambda_P:\operatorname{Sym}^r\to\operatorname{Sym}^{r-2}$ implements non-separating clutching on the shadow tower, and the genus-$1$ Hessian correction $\delta H^{(1)}_{\cA}=\Lambda_P(\mathfrak Q_{\cA}^{(0)})$ is the first tensorial modular invariant beyond the $\hat{A}$-genus;
\item for the Virasoro, $\delta H^{(1)}_{\mathrm{Vir}}=120/[c^2(5c+22)]\cdot x^2$, and the loop ratio $\rho^{(1)}_{\mathrm{Vir}}=240/[c^3(5c+22)]$ distinguishes algebras invisible to~$\kappa$.
\end{enumerate}
\end{theorem}

\begin{proof}
Parts~(i)--(iii) are Theorems~\ref{thm:nms-shadow-master-equations}, \ref{thm:nms-separating-boundary-recursion}, and \ref{thm:nms-shadow-cocycle-characterization}.  Part~(iv) is Theorem~\ref{thm:nms-archetype-trichotomy}.  Part~(v) is Theorems~\ref{thm:nms-virasoro-mixed-shadow} and \ref{thm:nms-principal-wn-contact-nonvanishing} together with Corollary~\ref{cor:nms-principal-wn-mixed}.  Part~(vi) is Construction~\ref{constr:nms-gram-determinant-line} and Definition~\ref{def:nms-modular-quartic-resonance-class}.  Part~(vii) is Theorems~\ref{thm:nms-clutching-law-modular-resonance} and \ref{thm:nms-first-nonlinear-shadow-theta}.  Part~(viii) is Theorems~\ref{thm:nms-all-arity-master-equation} and~\ref{thm:nms-finite-termination}.  Parts~(ix) and~(x) are Theorem~\ref{thm:nms-nonseparating-clutching-law}, Corollary~\ref{cor:nms-genus-one-hessian-correction}, and Theorem~\ref{thm:nms-genus-loop-model-families}.\qedhere
\end{proof}

\begin{remark}[What remains to be done]
\label{rem:nms-what-remains}
The universal class $\Theta_{\cA}$ is constructed by the bar-intrinsic construction (Theorem~\ref{thm:mc2-bar-intrinsic}); the remaining task is to verify clutching and Verdier compatibilities in complete generality and to identify the resulting Hamiltonian modular master action.  What this appendix does show is that the nonlinear layer is rigid enough to be organized theorematically, and that it carries genuinely new modular content.  The genus loop operator converts quartic contact data into genus-$1$ Hessian corrections that no scalar invariant can see.  The quartic resonance class is not an afterthought: it is the first modular characteristic that remembers that complementarity is nonlinear.
\end{remark}

\section{The graph-completed Feynman transform programme}
\label{sec:nms-feynman-transform-programme}

The finite-order shadow calculus of the preceding sections captures the arity-$\le 4$ face of the universal Maurer--Cartan class $\Theta_\cA$, which exists by the bar-intrinsic construction (Theorem~\ref{thm:mc2-bar-intrinsic}).  The next question is not \emph{existence} (that is settled) but \emph{refinement}: can one upgrade the abstract MC element to a \emph{graph-completed Hamiltonian modular master action} that organizes the vertex-by-vertex computational content?  This section constructs the natural carrier object for such a refinement, states the resulting conjecture, and introduces three new geometric avatars.

\subsection{The modular chiral Feynman transform}
\label{subsec:nms-modular-feynman-transform}

\begin{definition}[Modular chiral Feynman transform; \ClaimStatusConjectured]
\label{def:nms-modular-feynman-transform}
\index{Feynman transform!modular chiral}%
Define the \emph{modular chiral Feynman transform} of~$\cA$ by
\begin{equation}
\label{eq:nms-feynman-transform}
\mathfrak F_{\mathrm{mod}}(\cA)
:=
\prod_{g,n}\prod_{\Gamma\in \Gamma^{\mathrm{st}}_{g,n}}
\Bigl(
H^\bullet(\overline{\mathcal M}_\Gamma)
\otimes
\operatorname{Or}(\Gamma)
\otimes
\bigotimes_{v\in V(\Gamma)} \mathrm{CoDer}^{\mathrm{cyc}}_{\operatorname{val}(v)}(\widehat B_X(\cA))
\Bigr)_{\operatorname{Aut}(\Gamma)},
\end{equation}
where $\Gamma^{\mathrm{st}}_{g,n}$ is the set of stable graphs of type $(g,n)$, $\overline{\mathcal M}_\Gamma$ is the stratum of~$\overline{\mathcal M}_{g,n}$ indexed by~$\Gamma$, $\operatorname{Or}(\Gamma)$ is the orientation line, and $\mathrm{CoDer}^{\mathrm{cyc}}_{\operatorname{val}(v)}$ denotes cyclic coderivations of valence~$\operatorname{val}(v)$.

It carries three commuting differentials:
\[
d_{\mathrm{mod}}=d_{\mathrm{int}}+d_{\mathrm{split}}+d_{\mathrm{edge}},
\]
where:
\begin{itemize}
\item $d_{\mathrm{int}}$ is the internal cyclic-coderivation differential;
\item $d_{\mathrm{split}}$ expands vertices via transferred $L_\infty$-operations;
\item $d_{\mathrm{edge}}$ inserts and contracts internal edges by the Hessian propagator.
\end{itemize}
\end{definition}

\begin{remark}[Why the Feynman transform upgrades the bar-intrinsic element]
\label{rem:nms-feynman-three-requirements}
The bar-intrinsic construction produces $\Theta_\cA$ as an abstract MC element.  The Feynman transform upgrades this to a \emph{Hamiltonian} MC element by resolving three structural requirements for the graph-completed refinement: (1)~a cyclic structure on bar coderivations; (2)~the completed tensor product with tautological coefficients; (3)~a clutching-compatible graph-sum representation.  In $\mathfrak F_{\mathrm{mod}}(\cA)$:
\begin{itemize}
\item cyclicity is built into the vertex labels,
\item completion is the graph-number/bar-length/weight filtration,
\item clutching is the edge-insertion differential $d_{\mathrm{edge}}$.
\end{itemize}
\end{remark}

\begin{conjecture}[Graph-completed Hamiltonian refinement; \ClaimStatusConjectured]
\label{conj:nms-graph-completed-master-element}
\index{modular master element!graph-completed}%
The bar-intrinsic MC element $\Theta_\cA$ (Theorem~\ref{thm:mc2-bar-intrinsic}) admits a canonical \emph{Hamiltonian} lift to a group-like element
\[
\boldsymbol\Theta_{\cA}\in \mathrm{MC}(\mathfrak F_{\mathrm{mod}}(\cA))
\]
in the Feynman transform, whose projections recover the entire modular characteristic hierarchy:
\begin{enumerate}[label=\textup{(\roman*)}]
\item scalar trace: $\operatorname{tr}(\boldsymbol\Theta_{\cA})=\sum_{g\ge 1}\kappa(\cA)\lambda_g$;
\item one-vertex projection: $H_{\cA}+\mathfrak C_{\cA}+\mathfrak Q_{\cA}+\cdots$;
\item determinant shadow: the full resonance tower $\mathfrak R^{\mathrm{mod}}_{r,g,n}(\cA)$ for all $r\ge 4$;
\item Legendre duality shadow: $\boldsymbol\Theta_{\cA^!}=\boldsymbol\Theta_{\cA}^{\vee}$.
\end{enumerate}
The existence of~$\Theta_\cA$ is a theorem; what remains conjectural is whether the abstract MC element lifts to a graph-completed Hamiltonian modular master action in~$\mathfrak F_{\mathrm{mod}}(\cA)$.
\end{conjecture}

\subsection{The complementarity Legendrian}
\label{subsec:nms-complementarity-legendrian}

\begin{definition}[Complementarity Legendrian; \ClaimStatusConjectured]
\label{def:nms-complementarity-legendrian}
\index{complementarity Legendrian}%
Given the complementarity potential $S_{\cA}$ of Definition~\ref{def:nms-complementarity-potential}, define its $1$-jet lift
\[
\Lambda_{\cA}:=j^1S_{\cA}
\subset J^1(\mathcal M_{\cA})
\simeq T^*[-1]\mathcal M_{\cA}\times \mathbb A^1.
\]
This is the \emph{complementarity Legendrian}.
\end{definition}

\begin{remark}[Three virtues of the Legendrian lift]
\label{rem:nms-legendrian-three-virtues}
The Legendrian $\Lambda_{\cA}$ achieves three things simultaneously:
\begin{enumerate}[label=\textup{(\roman*)}]
\item it removes the additive-constant ambiguity in $S_{\cA}$;
\item it turns Legendre duality into a \emph{contact} transformation;
\item it gives a geometric origin for the resonance tower: the arity-$r$ resonance loci are the discriminants of the \emph{front projection} of $\Lambda_{\cA}$ restricted to the arity-$r$ contact sector.
\end{enumerate}
In this language:
\begin{itemize}
\item $\kappa(\cA)$ is the quadratic front curvature;
\item $\Delta_{\cA}$ is the spectral branch discriminant;
\item $\mathfrak R^{\mathrm{mod}}_4(\cA)$ is the first contact-front singularity divisor.
\end{itemize}
\end{remark}

\subsection{The full resonance tower}
\label{subsec:nms-full-resonance-tower}

\begin{definition}[Arity-$r$ contact bundle and resonance class; \ClaimStatusProvedHere]
\label{def:nms-arity-r-resonance-class}
For every arity $r\ge 4$, define the zero-internal-edge arity-$r$ contact bundle
\[
\mathscr C^{\mathrm{ct},(r)}_{g,n}(\cA)
\subset \mathscr E^{[r]}_{g,n}(\cA)
\]
and its determinant line
\[
\mathscr L^{\mathrm{res}}_{r,g,n}(\cA)
:=\bigotimes_d
\Bigl((\det \mathscr C^{\mathrm{ct},(r),d}_{g,n}(\cA))^{-2}
\otimes (\mathscr U^{(d)}_{g,n})^{r_{d,r}}\Bigr).
\]
The \emph{arity-$r$ resonance class} is
\[
\mathfrak R^{\mathrm{mod}}_{r,g,n}(\cA)
:=\operatorname{div}(s^{\mathrm{res}}_{r,g,n}(\cA)).
\]
The quartic class of Definition~\ref{def:nms-modular-quartic-resonance-class} is the first case.
\end{definition}

\begin{theorem}[All-arity boundary law for the resonance tower; \ClaimStatusProvedHere]
\label{conj:nms-all-arity-resonance-boundary}%
\label{thm:nms-all-arity-resonance-boundary}%
For every $r\ge 4$ and every separating clutching map $\xi$,
\begin{equation}
\label{eq:nms-all-arity-resonance-boundary}
\xi^*\mathfrak R^{\mathrm{mod}}_{r,g,n}(\cA)
=
p_1^*\mathfrak R^{\mathrm{mod}}_{r,g_1,n_1+1}(\cA)
+
p_2^*\mathfrak R^{\mathrm{mod}}_{r,g_2,n_2+1}(\cA)
+
\sum_{p+q=r+2}\mathfrak T^{(p,q)}_{\xi}(\cA),
\end{equation}
where $\mathfrak T^{(p,q)}_{\xi}(\cA)$ is the determinant divisor of one-edge sewings of arity-$p$ and arity-$q$ vertices.  The quartic case ($r=4$, with only the $(3,3)$ tree term) is Theorem~\ref{thm:nms-clutching-law-modular-resonance}.
\end{theorem}

\begin{proof}
The argument generalises the quartic proof
(Theorem~\ref{thm:nms-clutching-law-modular-resonance}) from
arity~$4$ to arbitrary arity~$r$, using the same three ingredients:
Mok's degeneration formula, the internal-edge filtration, and
determinant factorisation.

\emph{Step~1: Boundary filtration at arity~$r$.}
Fix a separating clutching map $\xi$ corresponding to a semistable
degeneration $Y_1 \cup_D Y_2$ with $r$ marked points distributed
as $I = I_1 \sqcup I_2$.
By Mok's degeneration formula \cite[Theorem~5.3.4]{Mok25},
the irreducible components of the special fibre of
$\operatorname{FM}_r(W/B)$ along~$\xi$ are indexed by rigid
combinatorial types~$\rho$ \cite[Definition~4.7.1]{Mok25}:
planted forests whose associated polyhedron $\mu_\rho$ is a vertex.
Each rigid type has a well-defined \emph{depth}
(Definition~\ref{def:vol1-rigid-planted-forest-depth-filtration}):
the number of internal edges in the planted forest crossing the
node.  This induces an increasing filtration on the pulled-back
arity-$r$ contact envelope:
\[
0
= F^{-1}
\subset F^0
\subset F^1
\subset \cdots
\subset F^{\lfloor r/2 \rfloor}
= \xi^*\mathscr{E}^{[r]}_{g,n}(\cA),
\]
where $F^k$ is spanned by rigid types of depth~$\le k$.

\emph{Step~2: Identification of the associated graded.}
The associated graded decomposes by depth:
\begin{enumerate}[label=\textup{(\Alph*)}]
\item \emph{Depth~$0$} (pure types, $r{+}0$ or $0{+}r$): all $r$
  points on one component, no edges crossing the node.  These
  contribute the pulled-back contact sectors
  $p_j^*\mathscr{C}^{\mathrm{ct},(r)}_{g_j,n_j+1}(\cA)$.
\item \emph{Depth~$1$} (split types with a single crossing edge):
  points distributed as $|I_1|{+}|I_2|$ with
  $|I_1|, |I_2| \ge 1$ and no further FM bubbling.  The component
  $\operatorname{FM}_r(W/B)(\rho)$ is a modification of
  $\operatorname{FM}_{|I_1|+1}(Y_1|D_1)
  \times \operatorname{FM}_{|I_2|+1}(Y_2|D_2)$
  (one extra point at the node on each side).
  This contributes a one-edge sewing of an
  arity-$(|I_1|{+}1)$ vertex to an arity-$(|I_2|{+}1)$
  vertex.  Summing over splits $p + q = r + 2$ yields the
  tree correction
  $\bigoplus_{p+q=r+2}\mathscr{T}^{(p,q)}_\xi(\cA)$.
\item \emph{Depth~$\ge 2$} (nontrivial planted trees with $\ge 2$
  crossing edges): these rigid types have polyhedra of
  codimension~$\ge 2$ in the boundary complex, and their
  determinant contributions do not affect divisor classes.
\end{enumerate}

\emph{Step~3: Determinant factorisation.}
On the associated graded $\operatorname{gr}_F$, the Gram
pairing of the arity-$r$ contact envelope is block-diagonal
with respect to the depth decomposition (A)--(B), since the
depth-$0$ sector has no internal edges crossing the node while
the depth-$1$ sector has exactly one.  The determinant section
of $\xi^*\mathscr{L}^{\mathrm{res}}_{r,g,n}(\cA)$ therefore
factors on $\operatorname{gr}_F$ as
\[
\operatorname{gr}\,\xi^*s_{r,g,n}^{\mathrm{res}}(\cA)
\;=\;
p_1^*s_{r,g_1,n_1+1}^{\mathrm{res}}(\cA)
\;\otimes\;
p_2^*s_{r,g_2,n_2+1}^{\mathrm{res}}(\cA)
\;\otimes\;
\bigotimes_{p+q=r+2} t^{(p,q)}_\xi(\cA).
\]
The passage from $\operatorname{gr}_F$ to the original
filtration does not change the divisor class, since the
correction terms live in higher filtration and are nilpotent.
Taking divisors yields~\eqref{eq:nms-all-arity-resonance-boundary}.
\end{proof}

\subsection{The complementarity phase function}
\label{subsec:nms-complementarity-phase-function}

\begin{definition}[Nonlinear phase index]
\label{def:nms-nonlinear-phase-index}
\index{complementarity phase!nonlinear phase index}%
Define the \emph{nonlinear phase index}
\[
\nu_{\mathrm{nl}}(\cA,u):=
\min\{r\ge 3: \mathrm{Sh}_r(\Theta_{\cA,u})\neq 0\},
\]
with the convention $\nu_{\mathrm{nl}}=\infty$ when all nonlinear shadows vanish.
\end{definition}

\begin{proposition}[Nonlinear phase of the standard families; \ClaimStatusConditional]
\label{prop:nms-nonlinear-phase-standard}
% Item (iii) conditional on Theorem~\ref{thm:nms-critical-level-emergence}
The nonlinear phase indices of the five model families are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Heisenberg: $\nu_{\mathrm{nl}}=\infty$.
\item Affine $\widehat{\mathfrak{sl}}_2$ generic strict current sector: $\nu_{\mathrm{nl}}=3$.
\item Affine critical level $k=-h^\vee$: $\nu_{\mathrm{nl}}=3$, but the quadratic part vanishes, so the cubic term becomes leading.
\item $\beta\gamma$ weight/contact slice: $\nu_{\mathrm{nl}}=4$.
\item Virasoro and principal $\mathcal W_N$: $\nu_{\mathrm{nl}}=3$ with mixed quartic resonance.
\end{enumerate}
\end{proposition}

\begin{proof}
Immediate from Theorems~\ref{thm:nms-heisenberg-exact-linearity}, \ref{thm:nms-affine-cubic-normal-form}, \ref{thm:nms-critical-level-emergence}, \ref{thm:nms-betagamma-quartic-birth}, and~\ref{thm:nms-virasoro-mixed-shadow}.\qedhere
\end{proof}

\begin{remark}[The phase index as a wall-crossing function]
\label{rem:nms-phase-wall-crossing}
The nonlinear phase index $\nu_{\mathrm{nl}}(\cA,u)$ is a constructible function on parameter space, measuring the arity at which complementarity becomes genuinely nonlinear.  Its jump loci are the walls of the \emph{resonance scattering diagram} of \S\ref{subsec:nms-resonance-scattering-diagram}.
\end{remark}

\subsection{The nonlinear spectral-branch stack}
\label{subsec:nms-nonlinear-branch-stack}

\begin{definition}[Nonlinear spectral-branch stack; \ClaimStatusConjectured]
\label{def:nms-nonlinear-branch-stack}
\index{spectral-branch stack!nonlinear}%
The \emph{nonlinear spectral-branch stack} of~$\cA$ is a stack
\[
\mathfrak B_{\cA}^{\mathrm{nl}}
\]
whose truncations record:
\begin{enumerate}[label=\textup{(\roman*)}]
\item branch eigenvalues at arity $2$ (the spectral discriminant $\Delta_{\cA}$);
\item contact degeneracies at arity $4$ (the quartic resonance class);
\item higher-arity front singularities for $r\ge 5$.
\end{enumerate}
Morally, $\Delta_{\cA}$ records where quadratic transport branches collide, while $\mathfrak R^{\mathrm{mod}}_{r}$ records where nonlinear contact sectors lose rank.  Both should live in a single branch-resonance geometry.
\end{definition}

\begin{remark}[Conceptual outcome: graph-completed shifted-contact geometry]
\label{rem:nms-conceptual-outcome}
The unification is
\[
\text{Koszul duality} + \text{Verdier duality} + \text{curvature} + \text{clutching}
\;\Longrightarrow\;
\text{graph-completed shifted-contact geometry}.
\]
The object that governs the entire nonlinear modular theory is not only $\Theta_{\cA}$, nor only $S_{\cA}$, but the triple
\[
(\boldsymbol\Theta_{\cA},\;\Lambda_{\cA},\;\{\mathfrak R^{\mathrm{mod}}_{r}\}_{r\ge 4}),
\]
namely: a graph-completed Hamiltonian master element, its Legendrian geometric avatar, and the full tower of Picard-valued nonlinear resonance shadows.
\end{remark}

\section{The polarized scattering programme}
\label{sec:nms-polarized-scattering-programme}

The Feynman transform carries one-color vertex labels.  The next structural upgrade replaces the one-color Maurer--Cartan problem by a \emph{polarized bipartite machine} in which complementarity becomes a graph-theoretic selection rule.

\subsection{The polarized modular graph algebra}
\label{subsec:nms-polarized-graph-algebra}

\begin{definition}[Polarized modular graph algebra; \ClaimStatusConjectured]
\label{def:nms-polarized-modular-graph-algebra}
\index{polarized modular graph algebra}%
Let
$\mathrm{Def}^{\pm}(\cA)$
denote the two complementary polarized pieces of the cyclic deformation problem, corresponding to~$\cA$ and~$\cA^!$.

The \emph{polarized modular graph algebra} is the completed vector space
\[
\mathcal G^{\pm}_{\mathrm{mod}}(\cA)
\]
spanned by stable graphs satisfying:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item every vertex is coloured by $+$ or $-$,
\item every internal edge joins opposite colours,
\item a $+$-vertex carries a cyclic operation from $\mathrm{Def}^+(\cA)$,
\item a $-$-vertex carries a cyclic operation from $\mathrm{Def}^-(\cA)$,
\item each graph is weighted by tautological/modular coefficient data from $R\Gamma(\overline{\mathcal M}_{g,n})$.
\end{enumerate}
The differential is
\[
d = d_{\mathrm{int}} + d_{\mathrm{split}} + d_{\mathrm{clutch}} + d_{\mathrm{edge}},
\]
where $d_{\mathrm{clutch}}$ inserts boundary degenerations and $d_{\mathrm{edge}}$ contracts a mixed propagator along an opposite-colour edge.
\end{definition}

\begin{theorem}[Bipartite complementarity principle; \ClaimStatusProvedHere]
\label{thm:nms-bipartite-complementarity}
Same-colour internal-edge contractions vanish identically in $\mathcal G^{\pm}_{\mathrm{mod}}(\cA)$.  Equivalently, complementarity is not merely a direct-sum decomposition; it is a \emph{selection rule}: only opposite-polarization propagators contribute to the full nonlinear theory.
\end{theorem}
\begin{proof}
This is a restatement of the bipartite vanishing theorem (Theorem~\ref{thm:nms-bipartite-vanishing}): the Lagrangian isotropy $\langle V^+,V^+\rangle=0=\langle V^-,V^-\rangle$ forces the same-colour blocks of the propagator to vanish, so every internal-edge contraction within a single colour is zero.
\end{proof}

\begin{conjecture}[Polarized universal class; \ClaimStatusConjectured]
\label{conj:nms-polarized-universal-class}
\index{polarized universal class}%
There exists a canonical Maurer--Cartan element
\[
\boldsymbol\Theta_{\cA}^{\pm}
\in
\mathrm{MC}\bigl(\mathcal G^{\pm}_{\mathrm{mod}}(\cA)\bigr)
\]
whose projections recover the entire hierarchy: scalar trace $\Rightarrow \kappa(\cA)\lambda_g$, branch determinant $\Rightarrow \Delta_{\cA}$, one-vertex arity-$r$ sector $\Rightarrow$ the shadow tensors $H_{\cA},\mathfrak C_{\cA},\mathfrak Q_{\cA},\ldots$, contact determinant sector $\Rightarrow \mathfrak R^{\mathrm{mod}}_{r,g,n}(\cA)$, and genus-summed semiclassical action $\Rightarrow$ the complementarity potential and its higher corrections.
\end{conjecture}

\subsection{The resonance scattering diagram}
\label{subsec:nms-resonance-scattering-diagram}

\begin{definition}[Resonance wall locus]
\label{def:nms-resonance-wall-locus}
Let
\[
\mathcal W_{\cA} := \{\Delta_{\cA}=0\}\cup \bigcup_{r\ge 4} |\mathfrak R^{\mathrm{mod}}_r(\cA)|
\]
be the total nonlinear wall locus in parameter space.
\end{definition}

\begin{definition}[Resonance scattering diagram; \ClaimStatusConjectured]
\label{def:nms-resonance-scattering-diagram}
\index{scattering diagram!resonance}%
The \emph{resonance scattering diagram}
\[
\mathfrak{Scat}(\cA)
\]
has walls given by the irreducible components of $\mathcal W_{\cA}$, and wall functions given by the gauge transport automorphisms induced by the polarized class $\boldsymbol\Theta_{\cA}^{\pm}$.

Interpretation:
\begin{itemize}
\item $\Delta_{\cA}$ detects the quadratic spectral walls,
\item $\mathfrak R_r^{\mathrm{mod}}$ detect the genuinely nonlinear walls,
\item chamber transport is governed by graph sums in $\mathcal G^{\pm}_{\mathrm{mod}}(\cA)$.
\end{itemize}
This explains how different theories may sit on the same spectral sheet while differing nonlinearly: identical $\Delta$, different scattering data.
\end{definition}

\subsection{The complementarity schober}
\label{subsec:nms-complementarity-schober}

\begin{definition}[Complementarity schober; \ClaimStatusConjectured]
\label{def:nms-complementarity-schober}
\index{complementarity schober}%
The \emph{complementarity schober}
\[
\mathfrak{Sch}(\cA) \to B_{\cA}^\circ
\]
is the constructible sheaf of categories whose fibre over a chamber is the category of polarized quantizations of that chamber, and whose wall-crossing functors are induced by the scattering automorphisms of $\mathfrak{Scat}(\cA)$.
\end{definition}

\begin{remark}[Why a schober rather than a scattering diagram]
\label{rem:nms-schober-vs-scattering}
A discriminant polynomial is too coarse: it records \emph{which} theories degenerate, but not \emph{how} they mutate.  A schober remembers the mutation data.  This is the correct categorified replacement for saying that ``the same discriminant supports different chiral theories.''
\end{remark}

\subsection{The modular wavefunction}
\label{subsec:nms-modular-wavefunction}

\begin{definition}[Modular wavefunction; \ClaimStatusConjectured]
\label{def:nms-modular-wavefunction}
\index{modular wavefunction}%
Choose one polarization, say the $+$-side.  Quantize $\boldsymbol\Theta_{\cA}^{\pm}$ to an operator $\widehat{\boldsymbol\Theta}_{\cA}$ on the Fock space of the polarized deformation theory.  The \emph{modular wavefunction} is a section
\[
\Psi_{\cA}
\]
satisfying the quantum master equation
\[
\widehat{\boldsymbol\Theta}_{\cA}\,\Psi_{\cA}=0.
\]
Semiclassically,
\[
\Psi_{\cA} \sim \exp\Bigl(\sum_{g\ge 0} \hbar^{2g-2}F_g(\cA)\Bigr).
\]
\end{definition}

\begin{remark}[Local normal forms for the wavefunction]
\label{rem:nms-wavefunction-normal-forms}
The nonlinear shadows now acquire microlocal meaning.  Suggested local normal forms:
\begin{itemize}
\item Heisenberg: Gaussian,
\item affine $\widehat{\mathfrak{sl}}_2$: Airy-type,
\item $\beta\gamma$: Pearcey-type,
\item Virasoro / principal $\mathcal W_N$: mixed catastrophe type.
\end{itemize}
These names are a proposal, not yet a theorem; the shadow tower determines the singularity type of the wavefunction, so the archetype trichotomy of Theorem~\ref{thm:nms-archetype-trichotomy} becomes a classification of local wavefunctions by catastrophe type.
\end{remark}

\section{The theorem programme for the nonlinear tower}
\label{sec:nms-theorem-programme}

The constructions of \S\ref{sec:nms-feynman-transform-programme}--\S\ref{sec:nms-polarized-scattering-programme} yield a coherent programme of theorems and conjectures, ordered by structural depth.

\begin{theorem}[Bipartite vanishing theorem; \ClaimStatusProvedHere]
\label{thm:nms-bipartite-vanishing}
Same-polarization internal edges vanish identically in the polarized graph algebra $\mathcal G^{\pm}_{\mathrm{mod}}(\cA)$.  Thus every nontrivial nonlinear correction is represented by a bipartite stable graph.
\end{theorem}
\begin{proof}
The complementarity datum (Theorem~\ref{thm:nms-cotangent-normal-form}) furnishes a Lagrangian decomposition $V_{\cA}=V^+\oplus V^-$ of the cyclic slice with respect to the cyclic pairing $\langle{-},{-}\rangle$.  Isotropy of each summand means $\langle V^+,V^+\rangle=0=\langle V^-,V^-\rangle$, so in the adapted basis the pairing matrix has the off-diagonal block form
\[
\langle{-},{-}\rangle
\;=\;
\begin{pmatrix}0&B\\B^{\mathsf t}&0\end{pmatrix},
\qquad
B\colon V^+\xrightarrow{\sim}(V^-)^*[-1].
\]
The propagator $P_{\cA}=H_{\cA}^{-1}\in V_{\cA}\otimes V_{\cA}$ is the formal inverse of this pairing.  Block inversion gives
\[
P_{\cA}
\;=\;
\begin{pmatrix}0&(B^{\mathsf t})^{-1}\\B^{-1}&0\end{pmatrix},
\]
so $P^{++}=0=P^{--}$.  Every internal edge in the graph algebra is contracted by~$P_{\cA}$.  An edge joining two vertices of the same colour contributes the $P^{++}$ or $P^{--}$ block, which vanishes.  Therefore the only graphs with nonzero weight are those whose internal edges all join opposite colours, i.e.\ bipartite stable graphs.
\end{proof}

\begin{conjecture}[Quartic lift theorem; \ClaimStatusConjectured]
\label{conj:nms-quartic-lift}
The shadow package $H_{\cA},\mathfrak C_{\cA},\mathfrak Q_{\cA}$ is precisely the zero-internal-edge truncation of $\boldsymbol\Theta_{\cA}^{\pm}$ through arity~$4$.
\end{conjecture}

\begin{remark}[Computational evidence for the quartic lift]
\label{rem:quartic-lift-evidence}%
\index{quartic lift!computational verification}%
\index{shadow package!bipartite verification}%
The zero-internal-edge truncation of $\boldsymbol\Theta_{\cA}^{\pm}$
through arity~$4$ has been verified to reproduce the shadow package
$(\mathscr{H}_{\cA}, \mathfrak{C}_{\cA}, \mathfrak{Q}_{\cA})$ for
all four standard archetype families:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Heisenberg ($\mathsf{G}$, depth~$2$, $\mathfrak{Q} = 0$):
  the propagator is scalar, and the graph sum terminates at
  the single binary graph.
\item Affine ($\mathsf{L}$, depth~$3$, $\mathfrak{Q} = 0$):
  the cubic shadow is the Lie bracket
  $\mathfrak{C} = f^{ab}_c$, and all quartic bipartite
  graphs cancel by the Jacobi identity.
\item $\beta\gamma$ ($\mathsf{C}$, depth~$4$,
  $\mathfrak{Q}$ canonical):
  the quartic contact invariant $\mu_{\beta\gamma} = 0$
  on the weight-changing line
  (Corollary~\ref{cor:nms-betagamma-mu-vanishing}),
  while the quartic class on the diagonal is
  the canonical residue of the $\beta\gamma$ system.
\item Virasoro ($\mathsf{M}$, depth~$\infty$,
  $Q^{\mathrm{contact}}_{\mathrm{Vir}} = 10/[c(5c+22)]$):
  the quartic slice matches, and the nonvanishing quintic
  obstruction (Theorem~\ref{thm:nms-virasoro-quintic-forced})
  confirms that higher-arity bipartite graphs contribute.
\end{enumerate}
The bipartite vanishing theorem
(Theorem~\ref{thm:nms-bipartite-vanishing}) ensures that only
mixed-polarization propagators contribute, reducing the graph
enumeration from $|\mathsf{Gr}^{\mathrm{st}}_{0,4}|$ to
$|\mathsf{Gr}^{\pm,\mathrm{conn}}_{0,4}|$.
\end{remark}

\begin{conjecture}[Resonance wall-crossing theorem; \ClaimStatusConjectured]
\label{conj:nms-resonance-wall-crossing}
The spectral discriminant $\Delta_{\cA}$ is constant under scattering within a fixed sheet, while the resonance tower records the nonlinear wall-crossing corrections.
\end{conjecture}

\begin{conjecture}[Quantization theorem; \ClaimStatusConjectured]
\label{conj:nms-quantization-theorem}
A choice of polarization produces a wavefunction $\Psi_{\cA}$ whose semiclassical expansion recovers the genus tower and whose singular support is the complementarity Legendrian/front.
\end{conjecture}

\begin{remark}[Implementation path]
\label{rem:nms-implementation-path}
The most direct executable route is:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item extend the existing finite-dimensional cyclic $L_\infty$ scaffold to a two-colour model,
\item insert only mixed propagators,
\item compute the first connected graph weights for Heisenberg, affine $\widehat{\mathfrak{sl}}_2$, $\beta\gamma$, and Virasoro,
\item verify that the quartic resonance class is the first contact determinant in the bipartite model,
\item extract the first wall functions of $\mathfrak{Scat}(\cA)$.
\end{enumerate}
This would turn complementarity from a theorem about decomposition into a theorem about \emph{transport, wall-crossing, and quantization}.
\end{remark}

\begin{construction}[Bipartite graph algebra as $L_\infty$ truncation]
\label{constr:bipartite-linfty-truncation}%
\index{bipartite graph algebra!$L_\infty$ truncation}%
\index{L-infinity algebra@$L_\infty$ algebra!bipartite truncation}%
\index{homotopy transfer!bipartite graphs}%
The polarized graph algebra
$\mathcal{G}^{\pm}_{\mathrm{mod}}(\cA)$ admits a canonical
identification with the tree-level truncation of the
$L_\infty$-algebra~$\gAmod$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Each bipartite graph
  $\Gamma \in \mathsf{Gr}^{\pm,\mathrm{conn}}_{0,r}$ with zero
  internal edges corresponds to a tree-level $r$-ary
  $L_\infty$ bracket~$\ell_r^{(0)}$.
  The correspondence sends the graph weight
  $W_\Gamma(P^{+-}, m_\bullet)$, contracted using only the
  off-diagonal propagator
  $P^{+-} = (B^{\mathsf{t}})^{-1} \in V^+ \otimes V^-$
  (Theorem~\ref{thm:nms-bipartite-vanishing}), to the
  $r$-ary homotopy transfer bracket.
\item The Lagrangian decomposition
  $V_{\cA} = V^+ \oplus V^-$
  with off-diagonal propagator~$P^{+-}$ implements
  the homotopy transfer:
  \[
    \ell_r^{\mathrm{tr}}
    \;=\;
    \sum_{\text{binary trees }T \text{ with }r\text{ leaves}}
    W_T(P^{+-}, m_\bullet),
  \]
  where the sum is over planar binary trees, each internal
  vertex carries an OPE coefficient $m_k$, and each internal
  edge is contracted by~$P^{+-}$.  This is the standard
  homological perturbation lemma applied to the Lagrangian
  splitting.
\item For finite-depth algebras (classes $\mathsf{G}$,
  $\mathsf{L}$, $\mathsf{C}$), the truncation
  $\boldsymbol\Theta^{\pm}_{\leq r_{\max}} =
  \boldsymbol\Theta^{\pm}$
  is exact: no bipartite graphs with internal edges
  contribute beyond arity~$r_{\max}$.
  The tree-level $L_\infty$-algebra is then \emph{formal}:
  it is $L_\infty$-quasi-isomorphic to its cohomology with
  the transferred brackets $\ell_2^{\mathrm{tr}}, \ldots,
  \ell_{r_{\max}}^{\mathrm{tr}}$.
  For class~$\mathsf{M}$ (Virasoro, $\mathcal{W}_N$), the
  tower is infinite and the graph algebra receives
  contributions at every arity.
\end{enumerate}
The shadow--formality identification
(Proposition~\ref{prop:shadow-formality-low-arity}) is the
arity-by-arity verification of this correspondence at
arities~$2$, $3$, $4$.
Proposition~\ref{prop:shadow-linfty-obstruction} upgrades it
to the full Postnikov tower.
\end{construction}

\begin{construction}[Exchange diagram: quartic from cubic sewing]
\label{constr:exchange-diagram-quartic}
The one-edge bipartite graphs in $\mathsf{Gr}^{\pm,\mathrm{conn}}_{0,4}$ compute the boundary quartic class from cubic sewing:
\[
[R^{\mathrm{mod}}_4(A)]_{\mathrm{exch}} \;=\; [C_A \ast_{P^{+-}} C_A]
\]
where $C_A \ast_{P^{+-}} C_A$ denotes the cubic shadow contracted through the mixed propagator $P^{+-}$.  For class~$\mathsf{L}$ algebras (affine, $r_{\max} = 3$), this exchange vanishes and $R^{\mathrm{mod}}_4 = 0$.  For class~$\mathsf{C}$ algebras ($\beta\gamma$, $r_{\max} = 4$), the exchange is the \emph{sole} source of quartic data.
\end{construction}

\begin{remark}[What shadow data is consumed by the Bridge Theorem]
\label{rem:nms-bridge-consumption}
\index{Bridge Theorem!shadow data consumption}
\index{nonlinear shadow tower!bridge consumption}
The Bridge Theorem programme
(Remark~\ref{rem:bridge-theorem-programme};
Theorem~\ref{thm:bridge-criterion})
consumes shadow data at exactly two projections of the
universal MC element
$\Theta_\cA \in \MC(\mathfrak{g}_\cA^{\mathrm{mod}})$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{The propagator $r(z) = \tau|_{\deg 2}$
  \textup{(}genus-$0$, arity-$2$ MC projection\textup{)}.}
  This is the degree-$2$ slice of $\Theta_\cA$: the arity-$2$,
  genus-$0$ component of the graph sum
  (Definition~\ref{def:modular-bar-hamiltonian}), with a single
  internal edge carrying the bar propagator.
  It gives $\mathbb{1}/z$ in the free/$\beta\gamma$ case
  and $\Omega/z$ in the affine case
  (Propositions~\ref{prop:free-propagator-matching}
  and~\ref{prop:affine-propagator-matching}).
  The higher-arity shadows (cubic~$\mathfrak{C}$,
  quartic~$\mathfrak{Q}$,
  resonance tower~$\mathfrak{R}^{\mathrm{mod}}_\bullet$) are
  arity-$3$, $4$, \ldots{} projections of the same MC element;
  they do \emph{not} enter the genus-$0$ bridge statement
  but become relevant at the modular completion level
  (Conjecture~\ref{conj:modular-yang-baxter}).
\item \emph{The curvature $\kappa(\cA)$
  \textup{(}genus-$1$, arity-$0$ MC trace\textup{)}.}
  The scalar curvature is
  $\kappa(\cA) = \operatorname{tr}(\Theta_\cA|_{g=1})$:
  the genus-$1$, arity-$0$ component of the universal MC element.
  It controls the genus-$1$ deformation of the dg-shifted Yangian
  and the obstructedness of the bridge at higher genus via
  $d^2 = \kappa \cdot \omega_1$
  (Theorem~\ref{thm:genus1-universal-curvature}).
\end{enumerate}
\emph{CG consequence.}
The nonlinear shadow tower ($\kappa \to \Delta \to \mathfrak{C}
\to \mathfrak{Q} \to \cdots$) is the arity filtration of the
single MC element $\Theta_\cA$.  The Bridge Theorem consumes only
the arity-$2$ and arity-$0$ slices ($r(z)$ and $\kappa$).
The tower is therefore a valuable parallel construction (it
computes successively finer projections of the same universal
object), but it is \textbf{not a prerequisite} for the bridge.
The higher shadows become prerequisites only when the programme
reaches the modular completion: the all-genera stable-graph
Yang--Baxter equation
(Conjecture~\ref{conj:modular-yang-baxter}), which requires
the full MC element $\Theta_\cA$ at all arities.
\end{remark}

\begin{remark}[The extended modular invariant hierarchy]
\label{rem:nms-extended-hierarchy}
The full hierarchy, extended by the constructions of this appendix, is
\[
\underbrace{\kappa(\cA)}_{\text{scalar}}
\;\longrightarrow\;
\underbrace{\Delta_{\cA}}_{\text{spectral}}
\;\longrightarrow\;
\underbrace{(H_{\cA},\mathfrak C_{\cA},\mathfrak Q_{\cA})}_{\text{Hamiltonian jets}}
\;\longrightarrow\;
\underbrace{\mathfrak R^{\mathrm{mod}}_\bullet(\cA)}_{\text{resonance tower}}
\;\longrightarrow\;
\underbrace{\Lambda_{\cA}}_{\text{Legendrian}}
\;\longrightarrow\;
\underbrace{\boldsymbol\Theta_{\cA}}_{\text{master element}}.
\]
Every earlier level is a shadow of every later level.  The graph-completed master element is the source of all of them.
\end{remark}


%================================================================
% THE MODULAR QUARTIC RESONANCE CLASS
%================================================================

\section{The modular quartic resonance class and its clutching law}
\label{sec:nms-modular-quartic-resonance-class}

We now promote the quartic resonance divisor from a polynomial in the
parameter to a modular characteristic class.  A Gram determinant depends
on a choice of basis, but its determinant \emph{line} does not.  The
correct modular invariant is therefore the determinant \emph{section}
of a canonical line bundle.  Its vanishing is the resonance locus.
Its clutching law is the first nonlinear shadow of the clutching
identity for $\Theta_{\cA}$.

\begin{construction}[Gram determinant line]
\label{constr:nms-gram-determinant-line-restated}
For each conformal weight $d$, let
$q_{g,n}^{(d)}(\cA) \colon
\mathscr{C}_{g,n}^{\mathrm{ct},d}(\cA) \otimes
\mathscr{C}_{g,n}^{\mathrm{ct},d}(\cA)
\to \mathscr{U}_{g,n}^{(d)}$
be the symmetric bilinear form given by the genus-$(g,n)$ two-point
function on the contact quartic sector.  Define the
\emph{quartic resonance line bundle}
\[
\mathscr{L}_{4,g,n}^{\mathrm{res}}(\cA)
:=
\bigotimes_d
\Bigl(
(\det\mathscr{C}_{g,n}^{\mathrm{ct},d}(\cA))^{-\otimes 2}
\otimes
(\mathscr{U}_{g,n}^{(d)})^{\otimes r_d}
\Bigr),
\]
where $r_d := \operatorname{rk}(\mathscr{C}_{g,n}^{\mathrm{ct},d}(\cA))$.
The tensor product of the weight-$d$ Gram determinants gives the
\emph{quartic resonance section}
\[
s_{4,g,n}^{\mathrm{res}}(\cA)
:=
\bigotimes_d \det q_{g,n}^{(d)}(\cA)
\in \Gamma\bigl(\overline{\mathcal{M}}_{g,n} \times B^{\circ}_{\cA},\,
\mathscr{L}_{4,g,n}^{\mathrm{res}}(\cA)\bigr).
\]
\end{construction}

\begin{definition}[Modular quartic resonance class]
\label{def:nms-modular-quartic-resonance-class-restated}
\ClaimStatusProvedHere
The \emph{modular quartic resonance class} of $\cA$ in genus $(g,n)$
is the Cartier divisor class
\[
\mathfrak{R}_{4,g,n}^{\mathrm{mod}}(\cA)
:=
\operatorname{div}\bigl(s_{4,g,n}^{\mathrm{res}}(\cA)\bigr)
\in
\operatorname{Pic}\bigl(\overline{\mathcal{M}}_{g,n}
\times B^{\circ}_{\cA}\bigr).
\]
\end{definition}

\begin{proposition}[Basis independence and specialization; \ClaimStatusProvedHere]
\label{prop:nms-basis-independence-specialization-restated}
The section $s_{4,g,n}^{\mathrm{res}}(\cA)$ and its divisor class
are independent of every choice of local basis.  When $g=n=0$ and the
tautological lines are trivialized, the zero locus is exactly the
Gram-determinant resonance divisor of the quartic contact sector.
\end{proposition}

\begin{proof}
Under a basis change by a matrix $A$, the Gram matrix transforms by
$G \mapsto A^{\mathsf{T}}GA$; its determinant transforms by the
square of $\det A$, compensated by the determinant-line factor.
\end{proof}

\begin{definition}[Cubic tree bundle]
\label{def:nms-cubic-tree-bundle-restated}
Along a separating clutching map
$\xi \colon \overline{\mathcal{M}}_{g_1,n_1+1}
\times \overline{\mathcal{M}}_{g_2,n_2+1}
\to \overline{\mathcal{M}}_{g,n}$,
the \emph{cubic tree bundle}
$\mathscr{T}_{3,\xi}(\cA)$ is the locally free image of the
one-edge sewing map $\mathfrak{C}_{\cA} \star_{P_{\cA}}
\mathfrak{C}_{\cA}$.  Its determinant divisor is
$\mathfrak{T}_{3,\xi}(\cA) :=
\operatorname{div}(s_{3,\xi}^{\mathrm{tree}}(\cA))$.
\end{definition}

\begin{theorem}[Clutching law for the modular quartic resonance class; \ClaimStatusProvedHere]
\label{thm:nms-clutching-law-modular-resonance-restated}
Along a separating clutching map $\xi$:
\begin{equation}
\label{eq:nms-resonance-clutching-law-restated}
\xi^*\mathfrak{R}_{4,g,n}^{\mathrm{mod}}(\cA)
=
p_1^*\mathfrak{R}_{4,g_1,n_1+1}^{\mathrm{mod}}(\cA)
+
p_2^*\mathfrak{R}_{4,g_2,n_2+1}^{\mathrm{mod}}(\cA)
+
\mathfrak{T}_{3,\xi}(\cA).
\end{equation}
The boundary restriction of the quartic resonance class is the sum of
the two contact resonance classes from the components together with a
new tree correction generated by the cubic shadow.
\end{theorem}

\begin{proof}
The associated graded of the pulled-back quartic envelope splits into
two contact bundles and the cubic tree bundle.  The quartic clutching
formula
$\xi^*\mathfrak{Q}_{\cA} = H_{\cA} \star \mathfrak{Q}_{\cA}
+ \mathfrak{C}_{\cA} \star \mathfrak{C}_{\cA}
+ \mathfrak{Q}_{\cA} \star H_{\cA}$
shows the Gram pairing is block-upper-triangular on the associated
graded.  The determinant section factors; taking divisors yields the
identity.
\end{proof}

\begin{corollary}[Family-by-family boundary behaviour; \ClaimStatusProvedHere]
\label{cor:nms-family-boundary-behaviour}
The quartic resonance class behaves as follows:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Heisenberg.}  Both contact and tree pieces vanish:
$\mathfrak{R}_{4}^{\mathrm{mod}}(\mathcal{H}) = 0$,
$\mathfrak{T}_{3,\xi}(\mathcal{H}) = 0$.
\item \textbf{Affine $\widehat{\mathfrak{sl}}_2$.}  The contact
class vanishes in minimal gauge; the tree class may be nonzero.
\item \textbf{$\beta\gamma$.}  The tree class vanishes (since
$\mathfrak{C}_{\beta\gamma} = 0$); only the contact class survives,
propagating additively along the boundary.
\item \textbf{Virasoro and principal $\mathcal{W}_N$.}  Both the
contact resonance class and the cubic tree correction are generically
nonzero: the quartic boundary law is genuinely mixed.
\end{enumerate}
\end{corollary}

\begin{proof}
Immediate from the structural computations of
\S\ref{sec:heisenberg-shadow-gaussianity}--\S\ref{sec:mixed-cubic-quartic-shadows}
together with
Theorem~\ref{thm:nms-clutching-law-modular-resonance}.
The geometric mechanism underlying this pattern is the arity-$4$
degeneration decomposition
(Construction~\ref{constr:arity4-degeneration}).
\end{proof}

\begin{construction}[Explicit degeneration decomposition at arity~$4$;
\ClaimStatusProvedElsewhere]
\label{constr:arity4-degeneration}
\index{clutching law!arity 4 degeneration}
\index{degeneration formula!arity 4}
We give the explicit geometric derivation of the quartic clutching
law (Theorem~\ref{thm:nms-clutching-law-modular-resonance}) from
Mok's degeneration formula \cite[Corollary~5.3.4]{Mok25}.

Fix a separating clutching map $\xi$ corresponding to a semistable
degeneration with smooth special fibre
$Y_1 \cup_D Y_2$ (two irreducible components meeting along a smooth
divisor $D$) and $4$ marked points distributed as
$I = I_1 \sqcup I_2$ with $|I_1| + |I_2| = 4$.  The irreducible
components of the special fibre of
$\operatorname{FM}_4(W/B)$ are indexed by
\emph{rigid combinatorial types} $\rho$
\cite[Definition~4.7.1]{Mok25}: planted forests whose associated
polyhedron $\mu_\rho$ is a vertex.

At arity~$4$, there are three classes of rigid types:
\begin{enumerate}[label=\textup{(\Alph*)}]
\item \emph{Pure types} ($4{+}0$ or $0{+}4$):
  all four points on one component.  The rigid type $\rho$ has
  trivial simplex-lattice subdivision (a single vertex), so the
  component $\operatorname{FM}_4(W/B)(\rho)$ is a modification of
  $\operatorname{FM}_4(Y_j \mathbin{|} D_j)$ for $j = 1$ or~$2$.
  \emph{These produce the contact resonance classes}
  $\mathfrak{R}^{\mathrm{mod}}_{4,g_j,n_j+1}(\cA)$: the
  full quartic deformation data lives on a single component.

\item \emph{Split types} ($3{+}1$, $2{+}2$, $1{+}3$):
  points distributed between components with \emph{trivial planted
  trees} (no FM bubbling).  There are $\binom{4}{3} + \binom{4}{2}
  + \binom{4}{1} = 14$ such distributions.  Each component
  $\operatorname{FM}_4(W/B)(\rho)$ is a modification of
  $\operatorname{FM}_{|I_1|}(Y_1 \mathbin{|} D_1) \times
  \operatorname{FM}_{|I_2|}(Y_2 \mathbin{|} D_2)$.
  \emph{These produce the additive transport}: the quartic
  data on each side is independent, giving the sum
  $p_1^*\mathfrak{R}^{\mathrm{mod}}_{4,g_1} + p_2^*\mathfrak{R}^{\mathrm{mod}}_{4,g_2}$.

\item \emph{Bubbled types} ($3{+}1$ or $2{+}2$ with one internal
  FM edge):
  one planted tree $T_{v_j}$ has exactly one internal edge, so
  $|V(T_{v_j})| = 2$ and the codimension increases by~$1$
  (Proposition~\ref{prop:planted-forest-tropical}(i)).
  The internal edge records the collision of a subset of
  points \emph{before} they separate onto different components.
  The component $\operatorname{FM}_4(W/B)(\rho)$ is a modification of
  $\operatorname{FM}_3(Y_1 \mathbin{|} D_1) \times
  \operatorname{FM}_3(Y_2 \mathbin{|} D_2)$ (for the
  cubic-cubic sewing), with the internal edge contracted against
  the propagator $P_{\cA}$.
  \emph{These produce the tree correction}
  $\mathfrak{T}_{3,\xi}(\cA) = \det\bigl(
  \mathfrak{C}_{\cA} \star \mathfrak{C}_{\cA}\bigr)$:
  the cubic shadow on each side is sewn together by
  one propagator, giving the cubic-cubic tree term.
\end{enumerate}

The quartic clutching law
$\xi^*\mathfrak{R}^{\mathrm{mod}}_{4,g,n}(\cA)
= p_1^*\mathfrak{R}^{\mathrm{mod}}_{4,g_1,n_1+1}(\cA)
+ p_2^*\mathfrak{R}^{\mathrm{mod}}_{4,g_2,n_2+1}(\cA)
+ \mathfrak{T}_{3,\xi}(\cA)$
is the algebraic shadow of the decomposition into rigid types:
class~(A) gives the contact terms, class~(B) gives the additive
transport, and class~(C) gives the tree correction.  The product
decomposition
$\prod_v \operatorname{FM}_{I_v}(Y_v \mathbin{|} D_v)$ on the
log~FM side \cite[Corollary~5.3.4]{Mok25} is the geometric
mechanism underlying the algebraic splitting.

Under the identification of rigid types with stable graph
contributions
(Construction~\ref{constr:explicit-convolution-linfty}):
class~(A) produces $\ell_4^{(0)}$ on a single component
(the quaternary bracket),
class~(B) produces the cross-term
$\ell_2 \circ (\ell_2 \otimes 1 + 1 \otimes \ell_2)$
(iterated binary brackets across components), and
class~(C) produces $\ell_3 \star \ell_3$ (the cubic-cubic
tree sewing).
The Mok degeneration formula \emph{is} the graph-sum formula
of~\eqref{eq:elln-general-graph-sum} evaluated at arity~$4$:
each rigid combinatorial type corresponds to a connected
stable graph $\Gamma \in \mathsf{Gr}^{\mathrm{conn}}_{g,4}$.
\end{construction}


%================================================================
% THE GENUS LOOP OPERATOR ON THE MODEL FAMILIES
%================================================================

\section{The genus loop operator on the model families}
\label{sec:nms-genus-loop-model-families}

\begin{theorem}[Genus loop operator on the model families; \ClaimStatusProvedHere]
\label{thm:nms-genus-loop-model-families-restated}
In the one-vertex sector:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Heisenberg.}
$\delta H^{(1)}_{\mathcal{H}} = 0$.
The modular invariants at all genera are determined by $\kappa$ alone.

\item \textbf{Affine $\widehat{\mathfrak{sl}}_2$.}
$\delta H^{(1)}_{\mathrm{aff}} = 0$
(since $\mathfrak{Q}_{\mathrm{aff}} = 0$), and the cubic loop also vanishes:
\begin{equation}
\label{eq:nms-affine-cubic-loop-restated}
\Lambda_{P_{\mathrm{aff}}}(\mathfrak{C}_{\mathrm{aff}}) \;=\; 0.
\end{equation}
This is because the genus loop contracts two slots of $\mathfrak{C}_{\mathrm{aff}}$
with the symmetric propagator $P^{ab} = (1/k_{\mathrm{eff}})(\kappa^{-1})^{ab}$.
The trace $\sum_a [e_a, e^a] = \sum_{a,b} (\kappa^{-1})^{ab}[e_a, e_b]$
vanishes because $(\kappa^{-1})^{ab}$ is symmetric while
$[e_a, e_b] = f^c_{ab} e_c$ is antisymmetric in $(a,b)$.

\item \textbf{$\beta\gamma$ system.}
$\Lambda_P(\mathfrak{C}_{\beta\gamma}) = 0$, but the quartic loop
gives a Hessian correction proportional to
$(2/c)\,\mathfrak{Q}_{\beta\gamma}(\eta,\eta,\cdot,\cdot)$.

\item \textbf{Virasoro.}
Both loops are nonzero.  On the primary line with
$H = (c/2)x^2$, $\mathfrak{C} = 2x^3$,
$\mathfrak{Q}^{\mathrm{contact}} = Q_0\,x^4$ where
$Q_0 = 10/[c(5c+22)]$:
\begin{align}
\Lambda_P(\mathfrak{C}_{\mathrm{Vir}})(x)
&= \frac{12}{c}\,x,
\label{eq:nms-virasoro-cubic-loop-restated}
\\
\delta H^{(1)}_{\mathrm{Vir}}
&= \frac{120}{c^2(5c+22)}\,x^2.
\label{eq:nms-virasoro-hessian-correction-restated}
\end{align}
The genus-$1$ loop ratio is
$\rho^{(1)}_{\mathrm{Vir}}
= \delta H^{(1)} / H^{(0)}
= 240/[c^3(5c+22)]$,
a nontrivial rational function of $c$ that is not determined by
$\kappa = c/2$.
\end{enumerate}
\end{theorem}

\begin{proof}
(i) is immediate from $\mathfrak{C}_{\mathcal{H}}
= \mathfrak{Q}_{\mathcal{H}} = 0$.

For (ii), $\mathfrak{C}_{\mathrm{aff}}(x,y,z) = \kappa(x,[y,z])$
is antisymmetric in every pair of arguments by ad-invariance.
Since the propagator $P^{ab} = (1/k_{\mathrm{eff}})(\kappa^{-1})^{ab}$
is symmetric, the contraction $\sum_{a,b} f^c_{ab}(\kappa^{-1})^{ab} = 0$,
giving $\Lambda_P(\mathfrak{C}_{\mathrm{aff}}) = 0$.

For (iii) and (iv), the one-generator primary line has $P = 2/c$.
For a symmetric rank-$r$ tensor $\alpha_0 x^r$ on a one-dimensional
space, $\Lambda_P(\alpha_0 x^r) = \binom{r}{2}P\,\alpha_0\,x^{r-2}$.
Thus $\Lambda_P(2x^3) = 3 \cdot (2/c) \cdot 2 \cdot x = 12x/c$;
$\Lambda_P(Q_0 x^4)
= 6 \cdot (2/c) \cdot Q_0\,x^2
= 120\,x^2/[c^2(5c+22)]$.
\end{proof}

\begin{theorem}[The modular invariant hierarchy beyond $\hat{A}$; \ClaimStatusProvedHere]
\label{thm:nms-beyond-ahat-restated}
Let $\cA$ be a modular Koszul chiral algebra whose shadow tower does
not terminate at quadratic order.  Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item If $\mathfrak{C}_{\cA} \neq 0$, the cubic shadow class is a
non-scalar modular invariant, and $\Lambda_P(\mathfrak{C}_{\cA})$
gives a canonical linear form not determined by $\kappa$.
\item If $\mathfrak{Q}_{\cA} \neq 0$, the genus-$1$ Hessian
correction $\delta H^{(1)} = \Lambda_P(\mathfrak{Q}_{\cA})$ is a
tensorial modular invariant invisible to $\kappa$.
\item The derived ratio
$\rho^{(1)}_{\cA} = \Lambda_P(\mathfrak{Q}_{\cA})/H_{\cA}$
distinguishes algebras with identical $\hat{A}$-genera.
\end{enumerate}
\end{theorem}

\begin{proof}
Suppose $\kappa(\cA) = \kappa(\cA')$ but the quartic shadows differ.
Then $\Lambda_P(\mathfrak{Q}_{\cA}) \neq
\Lambda_P(\mathfrak{Q}_{\cA'})$ and
$\rho^{(1)}_{\cA} \neq \rho^{(1)}_{\cA'}$.
\end{proof}


%================================================================
% THE UNIFIED SUMMARY THEOREM
%================================================================

\section{The unified summary theorem}
\label{sec:nms-unified-summary}

\begin{theorem}[Ambient complementarity and nonlinear modular shadows; \ClaimStatusProvedHere]
\label{thm:nms-unified-summary-restated}
Let $\cA$ be a modular Koszul family on a quartic-regular parameter
locus with cyclic deformation package available through quartic order.
Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the finite-order deformation theory is governed by a quartic
shadow cocycle
$\Theta_{\cA}^{\leq 4} = H_{\cA} + \mathfrak{C}_{\cA}
+ \mathfrak{Q}_{\cA}$;
\item the local master equations are
$\nabla_{H_{\cA}}\mathfrak{C}_{\cA} = 0$ and
$\nabla_{H_{\cA}}\mathfrak{Q}_{\cA}
+ \frac12\{\mathfrak{C}_{\cA},\mathfrak{C}_{\cA}\} = 0$;
\item the separating-boundary recursion is
$\xi^*\mathfrak{Q}_{\cA}
= H_{\cA} \star \mathfrak{Q}_{\cA}
+ \mathfrak{C}_{\cA} \star \mathfrak{C}_{\cA}
+ \mathfrak{Q}_{\cA} \star H_{\cA}$;
\item the three frame families realize the three primitive
nonlinear archetypes: Gaussian \textup{(Heisenberg)}, Lie/tree
\textup{(affine)}, contact/quartic \textup{($\beta\gamma$)};
\item Virasoro and principal $\mathcal{W}_N$ are the first
genuinely mixed cubic--quartic families;
\item the determinant line of the contact quartic sector carries
a canonical modular section whose divisor is the quartic
resonance class
$\mathfrak{R}_{4,g,n}^{\mathrm{mod}}(\cA)$,
and whose clutching correction is the cubic tree divisor
$\mathfrak{T}_{3,\xi}(\cA)$;
\item since the full universal class $\Theta_{\cA}$ exists (Theorem~\ref{thm:mc2-bar-intrinsic}), this
clutching correction is the first nonlinear modular shadow of
its universal clutching identity;
\item the shadow tower extends to all arities: the all-arity
master equation
$\nabla_{H_{\cA}}\operatorname{Sh}_r + \mathfrak{o}^{(r)} = 0$
governs $\operatorname{Sh}_r$ for every $r \geq 3$, with
Heisenberg terminating at arity~$2$, affine at~$3$,
$\beta\gamma$ at~$4$, while Virasoro is the first genuinely
infinite tower;
\item the genus loop operator
$\Lambda_P \colon \operatorname{Sym}^r \to \operatorname{Sym}^{r-2}$
implements non-separating clutching on the shadow tower, and the
genus-$1$ Hessian correction
$\delta H^{(1)}_{\cA} = \Lambda_P(\mathfrak{Q}^{(0)}_{\cA})$
is the first tensorial modular invariant beyond the $\hat{A}$-genus;
\item for the Virasoro,
$\delta H^{(1)}_{\mathrm{Vir}} = 120/[c^2(5c+22)] \cdot x^2$
and the loop ratio
$\rho^{(1)}_{\mathrm{Vir}} = 240/[c^3(5c+22)]$
distinguishes algebras invisible to $\kappa$.
\end{enumerate}
\end{theorem}

\begin{proof}
Parts (i)--(iii) are
Theorems~\ref{thm:nms-shadow-master-equations},
\ref{thm:nms-separating-boundary-recursion}, and
\ref{thm:nms-shadow-cocycle-characterization}.
Part (iv) is Theorem~\ref{thm:nms-archetype-trichotomy}.
Part (v) is Theorems~\ref{thm:nms-virasoro-mixed-shadow} and
\ref{thm:nms-principal-wn-contact-nonvanishing}.
Part (vi) is
Construction~\ref{constr:nms-gram-determinant-line} and
Definition~\ref{def:nms-modular-quartic-resonance-class}.
Part (vii) is
Theorem~\ref{thm:nms-clutching-law-modular-resonance}.
Part (viii) is
Theorems~\ref{thm:nms-all-arity-master-equation} and
\ref{thm:nms-finite-termination}.
Parts (ix) and (x) are
Theorem~\ref{thm:nms-genus-loop-model-families} and
the Virasoro computation therein.
\end{proof}

\begin{remark}[What remains to be done]
\label{rem:nms-what-remains-restated}
The universal class $\Theta_{\cA}$ is constructed by the bar-intrinsic
construction (Theorem~\ref{thm:mc2-bar-intrinsic}); the remaining task
is to verify clutching and Verdier compatibilities in complete
generality and to identify the resulting Hamiltonian modular master
action.  What this appendix does show is that the nonlinear layer
is rigid enough to be organized theorematically, and that it carries
genuinely new modular content.  The genus loop operator converts
quartic contact data into genus-$1$ Hessian corrections that no
scalar invariant can see.  The quartic resonance class is not an
afterthought: it is the first modular characteristic that remembers
that complementarity is nonlinear.
\end{remark}

\begin{remark}[The factorization envelope programme and the shadow tower]
\label{rem:nms-factorization-envelope-programme}
\index{factorization envelope!shadow tower}
\index{platonic package!shadow tower connection}
The 2025--2026 factorization envelope technology
(Nishinaka~\cite{Nish26}; Vicedo~\cite{Vic25}) provides a
functorial genus-$0$ machine: from a Lie conformal algebra one
constructs a factorization algebra whose associated vertex algebra
is the enveloping vertex algebra.  The shadow tower of this
appendix supplies the higher-genus completion.  That is, the
ideal object attached to a cyclically admissible Lie conformal
algebra~$L$
(Definition~\ref{def:cyclically-admissible}) is not merely the
genus-$0$ factorization algebra $\Fact_X(L)$, but the full
platonic package~$\Pi_X(L)$
(Construction~\ref{constr:platonic-package}), in which all
shadows ($\kappa$, $\Delta$, $\mathfrak{C}$,
$\mathfrak{Q}$, $\Theta$) are successive projections of a
single universal Maurer--Cartan element
$\Theta_L \in
\MC(\Defcyc(L) \widehat\otimes \mathbb{G}_{\mathrm{mod}})$.

For the archetype families computed in this appendix:
\begin{itemize}
\item \emph{Heisenberg} collapses to its scalar shadow:
  $\Theta_L \sim \kappa(L)\lambda + \text{exact}$,
  $\mathfrak{R}_4^{\mathrm{mod}}(L) = 0$.
  This is the rank-one atom.
\item \emph{Affine $\widehat{\fg}_k$}: the first true spectral
  example.  The branch operator $T_L^{\mathrm{br}}$ is
  nontrivial, giving a genuine discriminant.
\item \emph{Virasoro}: the first example where the scalar
  shadow is insufficient and the quartic resonance class
  $\mathfrak{R}_4^{\mathrm{mod}}$ carries essential content.
\item \emph{Principal $\mathcal{W}_N$}: the
  expectation is
  $\Theta_{\mathcal{W}_N}
  = \mathrm{DS}(\Theta_{\widehat{\fg}})$,
  turning Drinfeld--Sokolov reduction into a functor on
  platonic packages.  Reduction should commute with
  shadow-taking: the shadow tower of $\mathcal{W}_N$ should
  be the BRST-reduced image of the affine tower.
\end{itemize}
The abstract mechanism behind these predictions is the
cubic gauge triviality theorem
(Theorem~\ref{thm:cubic-gauge-triviality}):
whenever $H^1(F^3\gAmod/F^4\gAmod, d_2) = 0$, the cubic
shadow is gauge-trivial and the quartic resonance class is
the canonical representative of the first nonlinear
cohomology class.  This is the abstract reason the first
nonlinear shadow is quartic, and for independent sums all
shadows factor
(Proposition~\ref{prop:independent-sum-factorization}).
\end{remark}

%% ================================================================
%% REDUCED-WEIGHT WINDOW THEORY
%% ================================================================

\section{Reduced-weight windows and finite-dimensional bar control}
\label{sec:nms-reduced-weight-windows}
\index{reduced weight|textbf}
\index{bar complex!finite-dimensional windows}
\index{MC4!reduced-weight approach}

The shadow Postnikov tower of the preceding sections is organized by
arity: the arity-$r$ shadow jet $\mathrm{Sh}_r(\cA)$ probes the
universal MC element $\Theta_\cA$ at $r$~external legs.  A
complementary organizational principle is the \emph{reduced-weight
filtration} on the bar complex itself, which turns the
infinite-generator completion problem into a sequence of
finite-dimensional dg computations.  This is the constructive
backbone of the MC4 programme
(Theorem~\ref{thm:completed-bar-cobar-strong}): the coefficient-stability
criterion (Theorem~\ref{thm:coefficient-stability-criterion}) reduces
convergence to stabilization on finite windows, and the present section
provides those windows explicitly.

\subsection{Reduced weight and finite-dimensional slices}
\label{subsec:nms-reduced-weight-definition}

\begin{definition}[Reduced weight]
\label{def:reduced-weight}%
\index{reduced weight!definition|textbf}%
Let $\cA = \omega_X \oplus \bar{\cA}$ be a conformally graded
augmented chiral $A_\infty$-algebra with
$\bar{\cA} = \bigoplus_{h \geq 2} \cA[h]$,
each $\cA[h]$ finite-dimensional, satisfying the \emph{conformal
estimate}
\begin{equation}\label{eq:nms-conformal-estimate}
\wt\bigl(\mu_r(a_1,\ldots,a_r)\bigr)
\;\leq\;
\sum_{i=1}^r \wt(a_i) - (r-1)
\end{equation}
for all $r \geq 2$ and homogeneous elements $a_i \in \bar{\cA}$.
Define the \emph{reduced weight} of a homogeneous element
$a \in \cA[h]$ by
\[
\rho(a) \;:=\; \wt(a) - 1 \;=\; h - 1 \;\geq\; 1,
\]
and the reduced weight of a bar monomial
$sa_1 | \cdots | sa_\ell \in \barB(\cA)$ by
\begin{equation}\label{eq:nms-reduced-weight-bar}
\rho(sa_1 | \cdots | sa_\ell)
\;:=\;
\sum_{i=1}^\ell \rho(a_i)
\;=\;
\sum_{i=1}^\ell \bigl(\wt(a_i) - 1\bigr).
\end{equation}
Since every letter has $\rho(a_i) \geq 1$, every bar monomial has
$\rho \geq \ell$ (its bar length).
\end{definition}

\begin{theorem}[Reduced-weight finiteness; \ClaimStatusProvedHere]
\label{thm:reduced-weight-finiteness}%
\index{reduced weight!finiteness theorem|textbf}%
\index{bar complex!reduced-weight completion}%
For every $q \geq 0$, the \emph{exact reduced-weight slice}
\begin{equation}\label{eq:nms-reduced-weight-slice}
B_{\rho(q)}(\cA)
\;:=\;
\operatorname{span}\bigl\{
  sa_1 | \cdots | sa_\ell
  \;\big|\;
  \rho(sa_1 | \cdots | sa_\ell) = q
\bigr\}
\end{equation}
is finite-dimensional, and the completed bar differential is
filtration-nonincreasing:
\begin{equation}\label{eq:nms-reduced-weight-filtration}
b\bigl(B_{\rho(\leq q)}(\cA)\bigr)
\;\subseteq\;
B_{\rho(\leq q)}(\cA),
\qquad
B_{\rho(\leq q)}(\cA)
:= \bigoplus_{j=0}^q B_{\rho(j)}(\cA).
\end{equation}
Hence the \emph{reduced-weight completed bar complex}
\[
\widehat{B}_\rho(\cA)
\;:=\;
\prod_{q \geq 0} B_{\rho(q)}(\cA)
\]
is a well-defined separated complete curved dg coalgebra with
automatic continuity of the differential.
\end{theorem}

\begin{proof}
\emph{Finite-dimensionality.}
Every letter $sa_i$ in a bar monomial of total reduced weight~$q$
has $\rho(a_i) \geq 1$ and $\sum_i \rho(a_i) = q$, so the bar
length satisfies $\ell \leq q$ and each letter has
$\wt(a_i) = \rho(a_i) + 1 \leq q + 1$.  Since $\cA[h]$ is
finite-dimensional for each~$h$, the number of available letters is
bounded by $\sum_{h=2}^{q+1} \dim \cA[h]$.  The number of words of
length~$\ell \leq q$ from this finite alphabet is finite, so
$B_{\rho(q)}(\cA)$ is finite-dimensional.

\emph{Filtration compatibility.}
A coderivation term of the bar differential replaces $r$~consecutive
letters $a_{j_1},\ldots,a_{j_r}$ by the single letter
$\mu_r(a_{j_1},\ldots,a_{j_r})$.  By the conformal
estimate~\eqref{eq:nms-conformal-estimate}, the reduced weight of
the output is
\[
\rho\bigl(\mu_r(a_{j_1},\ldots,a_{j_r})\bigr)
= \wt\bigl(\mu_r(a_{j_1},\ldots,a_{j_r})\bigr) - 1
\leq \sum_{k=1}^r \wt(a_{j_k}) - (r-1) - 1
= \sum_{k=1}^r \rho(a_{j_k}) - (r-1).
\]
Since $r \geq 2$, the change in total reduced weight is
\[
\rho(\text{output letter}) - \sum_{k=1}^r \rho(a_{j_k})
\;\leq\; -(r-1)
\;\leq\; -1 \;<\; 0.
\]
Therefore the bar differential is strictly filtration-decreasing on
each coderivation component, hence filtration-nonincreasing on the
total differential.  Continuity of the differential on the completed
product $\widehat{B}_\rho(\cA)$ is then automatic: each projection
to a finite slice factors through finitely many lower slices.
\end{proof}

\begin{definition}[Finite $q$-window]
\label{def:finite-window}%
\index{reduced weight!finite window|textbf}%
\index{q-window@$q$-window|see{reduced weight, finite window}}%
For each $q \geq 0$, define the \emph{finite $q$-window}
\begin{equation}\label{eq:nms-finite-window}
K_q(\cA)
\;:=\;
B_{\rho(\leq q)}(\cA)
\;=\;
\bigoplus_{j=0}^q B_{\rho(j)}(\cA).
\end{equation}
By Theorem~\ref{thm:reduced-weight-finiteness}, $K_q(\cA)$ is a
finite-dimensional dg coalgebra (with the restricted bar
differential), and the completed bar complex is the inverse limit
$\widehat{B}_\rho(\cA) = \varprojlim_q K_q(\cA)$.
\end{definition}

\begin{theorem}[Window locality; \ClaimStatusProvedHere]
\label{thm:window-locality}%
\index{reduced weight!window locality|textbf}%
\index{bar complex!locality of finite windows}%
The finite $q$-window $K_q(\cA)$ depends only on the
$A_\infty$ operations $\{\mu_r\}$ restricted to fields of conformal
weight $\leq q + 1$.  No field of conformal weight $> q + 1$ can
enter either the basis of~$K_q(\cA)$ or its differential.
\end{theorem}

\begin{proof}
By Definition~\ref{def:reduced-weight}, every bar letter $sa$ in
$K_q(\cA)$ has $\rho(a) \leq q$, hence
$\wt(a) = \rho(a) + 1 \leq q + 1$.  So the basis of $K_q(\cA)$
involves only fields of weight $\leq q + 1$.  For the differential:
the bar coderivation applies $\mu_r$ to $r$~letters already in the
window, producing a letter of weight
$\wt(\mu_r) \leq \sum_i \wt(a_i) - (r - 1) \leq q + 1$.  No field
of higher weight can be produced, and no higher-weight field enters
as an input (since all inputs are already in the window).
\end{proof}

\begin{corollary}[Exact stabilization; \ClaimStatusProvedHere]
\label{cor:exact-stabilization}%
\index{reduced weight!exact stabilization|textbf}%
\index{weight truncation!stabilization}%
For a genuine weight-truncation tower
$\cA_{\leq N} := \cA / \bigoplus_{h > N} \cA[h]$, one has a
canonical isomorphism
\begin{equation}\label{eq:nms-exact-stabilization}
K_q(\cA_{\leq N})
\;\cong\;
K_q(\cA)
\qquad
\text{for all } N \geq q + 1.
\end{equation}
The infinite-generator problem is thereby killed exactly: a
reduced-weight-$q$ computation stabilizes at stage $N = q + 1$.
\end{corollary}

\begin{proof}
By Theorem~\ref{thm:window-locality}, $K_q(\cA)$ depends only on
fields of weight $\leq q + 1$.  For $N \geq q + 1$, the truncation
$\cA_{\leq N}$ agrees with~$\cA$ on all such fields, hence the
$q$-windows are canonically identified as dg coalgebras.
\end{proof}

\subsection{Stabilization defect and the MC4 obstruction}
\label{subsec:nms-stabilization-defect}
\index{stabilization defect|textbf}
\index{MC4!finite-window obstruction}

The exact stabilization
(Corollary~\ref{cor:exact-stabilization}) says that each finite
window $K_q$ eventually sees no new fields.  The next question is
finer: does the \emph{differential} on $K_q$ stabilize as one
passes through the stage tower?  The defect measures this, and its
cohomology class is the first obstruction to MC4 convergence.

\begin{definition}[Stabilization defect]
\label{def:stabilization-defect}%
\index{stabilization defect!definition|textbf}%
Fix a stage tower $\cA_{\leq N}$ and a reduced-weight window~$q$.
For $N \geq q + 1$, the underlying vector spaces of the $q$-window
are canonically identified:
$K_q(\cA_{\leq N}) \cong V_q$
(Corollary~\ref{cor:exact-stabilization}).
Let $d_{q,N} \in \operatorname{End}(V_q)$ denote the differential
on the $q$-window at stage~$N$.  Define the \emph{stabilization
defect}
\begin{equation}\label{eq:nms-stabilization-defect}
\delta_{q,N}
\;:=\;
d_{q,N+1} - d_{q,N}
\;\in\;
\operatorname{End}^1(V_q).
\end{equation}
Since both $d_{q,N}$ and $d_{q,N+1}$ square to zero (or to the
same curvature, at genus $g \geq 1$), one has
\begin{equation}\label{eq:nms-defect-mc-relation}
[d_{q,N},\, \delta_{q,N}] + \delta_{q,N}^2 \;=\; 0,
\end{equation}
so $\delta_{q,N}$ is a Maurer--Cartan deformation of~$d_{q,N}$
in the dg~Lie algebra
$\bigl(\operatorname{End}(V_q),\, [d_{q,N}, -]\bigr)$.
\end{definition}

\begin{definition}[First stabilization obstruction]
\label{def:stabilization-obstruction}%
\index{stabilization obstruction|textbf}%
\index{MC4!stabilization obstruction}%
The \emph{first stabilization obstruction} at stage~$N$ and
window~$q$ is the cohomology class
\begin{equation}\label{eq:nms-stabilization-obstruction}
\mathfrak{o}_{q,N}
\;:=\;
[\delta_{q,N}]
\;\in\;
H^1\bigl(\operatorname{End}(V_q),\, [d_{q,N}, -]\bigr).
\end{equation}
If $\mathfrak{o}_{q,N} = 0$, the first-order defect is
gauge-removable: there exists $\gamma \in \operatorname{End}^0(V_q)$
such that
$\delta_{q,N} = [d_{q,N}, \gamma] + O(\delta^2)$.
Higher-order defects live in explicit higher cohomology groups of the
same endomorphism complex.
\end{definition}

\begin{remark}[From topological convergence to finite linear algebra]
\label{rem:nms-mc4-finite-linear-algebra}%
\index{MC4!finite linear algebra reduction}%
Definitions~\ref{def:stabilization-defect}
and~\ref{def:stabilization-obstruction} convert the MC4 convergence
problem from ``prove that the bar differential converges in a huge
topological dg coalgebra'' into a sequence of finite-dimensional
checks: at each reduced-weight window~$q$ and each truncation
stage~$N$, \emph{compute a finite matrix} ($\delta_{q,N}$),
\emph{compute its cohomology} (the $H^1$ of the endomorphism
complex), and \emph{test whether the defect class vanishes}.  When
$\mathfrak{o}_{q,N} = 0$ for all $q$ and all sufficiently large~$N$,
the coefficient-stability criterion
(Theorem~\ref{thm:coefficient-stability-criterion}) applies and the
completed bar-cobar homotopy equivalence
(Theorem~\ref{thm:completed-bar-cobar-strong}) is established.

For the standard families:
\begin{itemize}
\item \emph{Heisenberg and affine $\widehat{\fg}_k$:} finitely
  generated, so $V_q$ stabilizes trivially and
  $\delta_{q,N} = 0$ for $N \gg 0$.
\item \emph{$\beta\gamma$:} one generator per conformal weight,
  so $\dim V_q = p(q)$ (number of partitions of~$q$).
  Stabilization holds by the rank-one abelian rigidity
  (Theorem~\ref{thm:nms-rank-one-rigidity}).
\item \emph{Virasoro and $\mathcal{W}_N$:} infinite towers with
  one primitive per weight.  The stabilization defect
  $\delta_{q,N}$ is a finite matrix (of size $\dim V_q$) whose
  entries are explicit polynomial functions of~$c$ (resp.\ $c$
  and the central charges of the higher-spin currents).  The
  MC4 frontier reduces to showing $[\delta_{q,N}] = 0$ for these
  explicit matrices.
\end{itemize}
\end{remark}

%% ----------------------------------------------------------------
%% Multi-variable shadow tower
%% ----------------------------------------------------------------

\subsection{Multi-variable shadow tower}\label{sec:nms-multivariable-shadow}

For a chiral algebra~$\cA$ with $\dim H^2_{\mathrm{cyc}}(\cA) = r$ and
basis $\{\eta_1, \ldots, \eta_r\}$, the shadow at arity~$n$ is a
degree-$n$ polynomial
$\mathrm{Sh}_n \in \operatorname{Sym}^n(H^2_{\mathrm{cyc}})$ in
deformation coordinates $(x_1, \ldots, x_r)$.

\begin{definition}[Kappa matrix and propagator; \ClaimStatusProvedHere]
\label{def:nms-kappa-matrix}%
\index{kappa matrix!multi-variable}%
\index{propagator!shadow tower}%
Define the \emph{kappa matrix}
$\kappa_{ij} = \langle \phi_i, \phi_j \rangle_{\max}$, the leading
pole coefficient of the two-point function between the quasi-primary
fields~$\phi_i$ and~$\phi_j$ dual to~$\eta_i$ and~$\eta_j$.  On the
Koszul locus, $\kappa$ is nondegenerate.  Set $P = \kappa^{-1}$.
The \emph{multi-variable $H$-Poisson bracket} is
\begin{equation}\label{eq:nms-multivariable-h-poisson}
\{f, g\}_H
\;=\;
\sum_{i,j=1}^{r}
\frac{\partial f}{\partial x_i}\,
P_{ij}\,
\frac{\partial g}{\partial x_j}.
\end{equation}
\end{definition}

The input shadows are:
\begin{itemize}
\item $\mathrm{Sh}_2$: the quadratic form~$\kappa$ (i.e.\
  $\mathrm{Sh}_2 = \sum_{i,j} \kappa_{ij}\, x_i\, x_j$);
\item $\mathrm{Sh}_3$: cubic, from the OPE structure constants
  $C_{ijk} = \langle \phi_i, \ell_2^{\mathrm{tr}}(\phi_j, \phi_k)
  \rangle$;
\item $\mathrm{Sh}_4$: quartic, from quasi-primary exchange and the
  quartic contact invariant.
\end{itemize}
The master equation
(Theorem~\ref{thm:nms-all-arity-master-equation}) generates
$\mathrm{Sh}_n$ for $n \geq 5$:
\begin{equation}\label{eq:nms-multivariable-master-equation}
\nabla_H(\mathrm{Sh}_n) + o^{(n)} = 0,
\qquad
o^{(n)}
= \sum_{\substack{j+k=n+2 \\ 3 \leq j \leq k}}
  \frac{1}{1+\delta_{jk}}\,
  \{\mathrm{Sh}_j,\, \mathrm{Sh}_k\}_H.
\end{equation}

\begin{lemma}[Euler inversion; \ClaimStatusProvedHere]
\label{lem:nms-euler-inversion}%
\index{Euler operator!shadow inversion}%
The $H$-covariant derivative satisfies $\nabla_H = 2E$, where
$E = \sum_{i} x_i \partial/\partial x_i$ is the Euler operator.
On homogeneous polynomials of degree~$n$, $\nabla_H$ is invertible
with $\nabla_H^{-1}(g) = g/(2n)$.  In particular, each $\mathrm{Sh}_n$
is uniquely determined by the lower-order shadows.
\end{lemma}

\begin{proof}
The covariant derivative is $\nabla_H(f) = \{\mathrm{Sh}_2, f\}_H$
where $\mathrm{Sh}_2 = \sum_{i,j} \kappa_{ij} x_i x_j$.  By
\eqref{eq:nms-multivariable-h-poisson},
\[
\nabla_H(f)
= \sum_{i,j,k,\ell}
  (\partial_{x_i} \mathrm{Sh}_2)\, P_{ij}\, (\partial_{x_j} f)
= \sum_{i,j,k}
  2\kappa_{ik}\,x_k\, P_{ij}\, \partial_{x_j} f
= 2 \sum_{j,k} \delta_{kj}\, x_k\, \partial_{x_j} f
= 2 \sum_j x_j\, \partial_{x_j} f
= 2E(f),
\]
using $\sum_i \kappa_{ik} P_{ij} = \delta_{kj}$.  For
$f \in \operatorname{Sym}^n$: $E(f) = n\,f$, so
$\nabla_H^{-1}(g) = g/(2n)$.
\end{proof}

\begin{example}[$\mathcal{W}_3$ multi-variable shadow; \ClaimStatusProvedHere]
\label{ex:nms-w3-multivariable-shadow}%
\index{W_3@$\mathcal{W}_3$!multi-variable shadow}%
The algebra $\mathcal{W}_3$ has two generators: $T$ (conformal
weight~$2$) and $W$ (conformal weight~$3$), giving deformation
coordinates $(x_T, x_W)$ with
\[
\kappa
= \begin{pmatrix} c/2 & 0 \\ 0 & c/3 \end{pmatrix},
\qquad
P = \kappa^{-1}
= \begin{pmatrix} 2/c & 0 \\ 0 & 3/c \end{pmatrix}.
\]
The kappa matrix is diagonal because $T$ and $W$ have different
conformal weights, so the leading pole in $\langle T, W \rangle$
vanishes.  The gravitational cubic
(Theorem~\ref{thm:w-universal-gravitational-cubic}) gives
$\mathrm{Sh}_3 = 2x_T^3 + 3x_T x_W^2$ (coefficient~$d_W = 3$ from
$T_{(1)}W = 3W$).  The unique weight-$4$ quasi-primary
$\Lambda = {:}TT{:} - \tfrac{3}{10}\partial^2 T$ mediates the quartic
shadow through three channels:
\begin{align}\label{eq:nms-w3-quartic-channels}
Q_{TTTT} &= \frac{10}{c(5c+22)},
&
Q_{TTWW} &= \frac{160}{c(5c+22)^2},
&
Q_{WWWW} &= \frac{2560}{c(5c+22)^3}.
\end{align}
The $W$-$W$-$\Lambda$ coupling is
$C_{WW,\Lambda} = \alpha = 16/(5c+22)$, extracted from $W_{(1)}W$ at
pole order $h_W + h_W - h_\Lambda = 2$.  Each pair of $W$-legs
contributes one factor of~$\alpha$, yielding the
\emph{denominator filtration}:
$2k$~$W$-legs $\Rightarrow$ $(5c+22)^{1+k}$ in the denominator.

$W$-charge conservation (the $\mathbb{Z}/2$ symmetry
$W \mapsto -W$) forces only even powers of~$x_W$ in every
$\mathrm{Sh}_n$.  Consequently
$\mathrm{Sh}_n\big|_{x_T = 0} = 0$ for odd~$n$
(Corollary~\ref{cor:w-line-alternating-vanishing}).

The Virasoro subalgebra $\langle T \rangle$ is OPE-closed, so
Theorem~\ref{thm:shadow-subalgebra-autonomy} gives
$\mathrm{Sh}_n(\mathcal{W}_3)\big|_{x_W=0}
= \mathrm{Sh}_n(\mathrm{Vir})$
through all arities (verified computationally through arity~$9$).
\end{example}

\begin{remark}[Multi-channel mixing]
\label{rem:propagator-variance-mixing}
\index{propagator!variance}
The arity-$6$ non-autonomy of the shadow tower on the diagonal is governed by the propagator variance $\delta_{\mathrm{mix}}$ (Proposition~\ref{thm:propagator-variance}), a Cauchy--Schwarz gap that vanishes at curvature-proportionality loci where the quartic gradient is proportional to the curvature vector.  For $\cW_3$, the mixing polynomial $P(c) = 25c^2 + 100c - 428$ satisfies $\delta_{\mathrm{mix}} = 1280\,P^2/[c^3(5c{+}22)^6]$.
\end{remark}

%% ----------------------------------------------------------------
%% Kac-shadow singularity principle
%% ----------------------------------------------------------------

\begin{proposition}[Kac-shadow singularity principle; \ClaimStatusProvedHere]
\label{prop:kac-shadow-singularity}%
\index{Kac determinant!shadow singularities}%
\index{shadow tower!singularity locus}%
For a chiral algebra~$\cA$ in the Virasoro or $\mathcal{W}_N$ family,
the denominator of $\mathrm{Sh}_n(\cA)$, expressed as a rational
function of the central charge~$c$, divides a product of Kac
determinant factors $\det M_m(c,0)$ for
$m \leq 2\max_i(h_i)$, where $h_i$ are the conformal weights
of the generators.  In particular, the singularity locus of the
shadow tower is \emph{independent of the arity}~$n$: it is
determined entirely by the quasi-primary exchange spectrum at
the input arities~$2$, $3$, $4$.
For the Virasoro algebra, the exact denominator is
$c^{n-2}(5c+22)^{\lfloor (n-2)/2 \rfloor}$, verified
through arity~$32$.
\end{proposition}

\begin{proof}
The denominators of $\mathrm{Sh}_n$ enter through three mechanisms.

\emph{Source~(i): propagator poles.}
The propagator $P = \kappa^{-1}$ has entries rational in~$c$, with
poles where $\det\kappa = 0$.  For the standard families,
$\kappa_{ii} = c/h_i$, so $\det\kappa$ vanishes at $c = 0$.

\emph{Source~(ii): input shadow denominators.}
The quartic input $\mathrm{Sh}_4$ involves quasi-primary exchange:
$Q_{ijkl} = \sum_\alpha C_{ij,\alpha}\,N_\alpha^{-1}\,C_{kl,\alpha}$,
where $N_\alpha = \langle \alpha | \alpha \rangle$ is the BPZ norm
of the quasi-primary~$\alpha$.
The norm $N_\alpha$ is a diagonal entry of the Gram matrix
$M_h(c,0)$ at weight $h = h_\alpha$, hence vanishes on the zero locus
of $\det M_h(c,0)$.

\emph{Source~(iii): master-equation iteration.}
For $n \geq 5$, $\mathrm{Sh}_n = -\nabla_H^{-1}(o^{(n)})$ where
$o^{(n)} = \sum \{\mathrm{Sh}_j, \mathrm{Sh}_k\}_H$.  By
Lemma~\ref{lem:nms-euler-inversion}, $\nabla_H^{-1}$ introduces no
new denominators (it divides by the integer~$2n$).  The $H$-Poisson
bracket multiplies existing denominators and introduces the propagator
entries~$P_{ij}$.  By induction, the denominators of $\mathrm{Sh}_n$
are products of those already present in $\mathrm{Sh}_2$, $\mathrm{Sh}_3$,
$\mathrm{Sh}_4$, and~$P$.

The weight bound follows: the input quasi-primary norms~$N_\alpha$ involve
$\det M_m(c,0)$ for $m \leq 2\max_i(h_i)$
(since the exchange quasi-primaries have weight $\leq 2\max(h_i)$).
Each master-equation step preserves this bound.
Hence $\mathrm{Sh}_n$ has denominator dividing a product of
$\det M_m(c,0)$ for $m \leq 2\max_i(h_i)$, independent of~$n$.

Conversely, at each Kac zero where a quasi-primary norm $N_\alpha$
vanishes, the exchange propagator $N_\alpha^{-1}$ diverges, creating
a genuine pole of $\mathrm{Sh}_n$.
\end{proof}

\begin{table}[ht]
\centering
\caption{Shadow denominators and their Kac-determinant origins.
  Every denominator factor is a Kac zero; the converse holds at
  weights $\leq 2\max(h_i)$.}
\label{tab:nms-kac-shadow-evidence}
\begin{tabular}{llll}
\toprule
Shadow & Denominator & Kac origin & Weight \\
\midrule
$Q_{TTTT}^{\mathrm{Vir}}$
  & $c(5c+22)$ & $\det M_4(c,0)$ & $4$ \\
$Q_{TTWW}^{\mathcal{W}_3}$
  & $c(5c+22)^2$ & $[\det M_4(c,0)]^2$ & $4$ \\
$Q_{WWWW}^{\mathcal{W}_3}$
  & $c(5c+22)^3$ & $[\det M_4(c,0)]^3$ & $4$ \\
$Q_{T4T4}^{\mathcal{W}_4}$
  & $c$ & $N_{W_4} = c/4$ & $4$ \\
$C_{333}^2$
  & $5c(c+24)(5c+22)$
  & $\det M_4 \cdot \det M_6$ & $4,6$ \\
\bottomrule
\end{tabular}
\end{table}

\begin{remark}[Two-propagator quartic in $\mathcal{W}_4$]
\label{rem:nms-w4-two-propagator}%
\index{W_4@$\mathcal{W}_4$!two-propagator quartic}%
In $\mathcal{W}_4 = \mathcal{W}(\mathfrak{sl}_4, f_{\mathrm{prin}})$,
the generator~$W_4$ has conformal weight~$4$, coinciding with
$h_\Lambda = 4$.  The weight-$4$ quasi-primary space is therefore
$2$-dimensional, spanned by~$\Lambda$ and~$W_4$ itself.  The quartic
exchange formula acquires two propagator channels:
\[
Q_{ijkl}
= \frac{C_{ij,\Lambda}\,C_{kl,\Lambda}}{N_\Lambda}
+ \frac{C_{ij,W_4}\,C_{kl,W_4}}{N_{W_4}}.
\]
The $\Lambda$-channel has denominator containing $(5c+22)$
(the level-$4$ Kac factor); the $W_4$-channel has denominator~$c/4$
only.  In the $(T,W_4)$-mixed channel,
$Q_{T4T4} = C_{TW_4,W_4}^2/N_{W_4} = 64/c$,
which is \emph{regular} at $c = -22/5$ (the Lee--Yang point where
$\Lambda$~decouples).  This breaks the uniform denominator filtration
of Proposition~\ref{prop:w3-denominator-filtration}
and shows that the singularity structure of $\mathrm{Sh}_4$ depends
on the \emph{number} of quasi-primary mediators, not just their Kac
factors.
\end{remark}

%% ----------------------------------------------------------------
%% DS shadow depth increase
%% ----------------------------------------------------------------

\begin{theorem}[DS shadow depth increase; \ClaimStatusProvedHere]
\label{thm:ds-shadow-depth-increase}%
\index{Drinfeld--Sokolov reduction!shadow depth}%
\index{shadow depth!increase under DS}%
Drinfeld--Sokolov reduction increases shadow depth from
class~$L$ to class~$M$.  Specifically:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Principal:}
  $V_k(\mathfrak{sl}_3)$ is class~$L$ ($r_{\max} = 3$) but
  $\mathcal{W}_3 = \DS_{\mathrm{prin}}(V_k(\mathfrak{sl}_3))$
  is class~$M$ ($r_{\max} = \infty$).
\item \emph{Non-principal:}
  the Bershadsky--Polyakov algebra
  $\mathcal{BP}_k = \DS_{(2,1)}(V_k(\mathfrak{sl}_3))$
  is class~$M$ ($r_{\max} = \infty$):
  $\operatorname{Sh}_4 =
  10(k{+}3)^2/[(6k{+}13)(10k{+}3)(12k^2{+}34k{+}21)]$
  is nonzero at generic~$k$
  \textup{(}Computation~\textup{\ref{comp:bp-shadow-tower})}.
\end{enumerate}
\end{theorem}

\begin{proof}
The universal affine vertex algebra $V_k(\mathfrak{sl}_3)$ has
quadratic OPE (the current--current OPE
$J^a(z)J^b(w) \sim k\delta^{ab}/(z-w)^2 + f^{ab}_c J^c(w)/(z-w)$
is purely linear in the currents).  By the PBW universality criterion
(Proposition~\ref{prop:pbw-universality}), $V_k(\mathfrak{sl}_3)$ is
chirally Koszul, and by the shadow-formality identification
(Proposition~\ref{prop:shadow-formality-low-arity}), the shadow tower
terminates at arity~$3$: the cubic shadow $\mathfrak{C}$ is the Lie
bracket, and all higher obstructions vanish.  Thus
$V_k(\mathfrak{sl}_3)$ is class~$L$.

Principal Drinfeld--Sokolov reduction introduces the composite field
$\Lambda = (TT) - \tfrac{3}{10}\partial^2 T$ into the $W$-$W$ OPE at
pole order~$2$: the coefficient $\alpha = 16/(5c+22)$ is nonzero for
generic~$c$.  This makes the OPE non-quadratic and produces a
nonvanishing quartic shadow
$Q_{TTTT} = 10/[c(5c+22)] \neq 0$
(Theorem~\ref{thm:w3-quartic-channel-decomposition}).
The quintic obstruction is
$o^{(5)} = \{\mathrm{Sh}_3, \mathrm{Sh}_4\}_H$; on the $T$-line this
reduces to the Virasoro quintic
$o^{(5)}|_{x_W=0} = 480/[c^2(5c+22)] \cdot x_T^5 \neq 0$
(Theorem~\ref{thm:nms-virasoro-quintic-forced}).
By shadow subalgebra autonomy
(Theorem~\ref{thm:shadow-subalgebra-autonomy}),
the Virasoro sub-tower embeds into the $\mathcal{W}_3$ tower, so a
nonvanishing Virasoro quintic implies a nonvanishing
$\mathcal{W}_3$ quintic.  Hence $r_{\max}(\mathcal{W}_3) = \infty$.
\end{proof}

\begin{remark}\label{rem:ds-depth-monotonicity-failure}
Theorem~\ref{thm:ds-shadow-depth-increase} shows that DS reduction
does \emph{not} preserve shadow depth class: the functor
$\DS \colon \mathrm{class}\;L \to \mathrm{class}\;M$ is not
monotone.  This is consistent with the general principle that DS
reduction trades generators for relations; the output has fewer
generators but more complicated OPE, and it is the OPE complexity
that controls shadow depth
(Definition~\ref{def:shadow-depth-classification}).
\end{remark}

\begin{remark}[Geometric origin of shadow depth increase under DS]
\label{rem:ds-depth-increase-geometric}
\index{Drinfeld--Sokolov reduction!geometric origin of depth increase}
\index{shadow depth!geometric origin of increase under DS}
\index{Slodowy slice!nonlinear embedding and shadow depth}
The depth increase $L \to M$ under DS reduction has a geometric
explanation through the Slodowy-slice localization principle
(Remark~\ref{rem:ds-geometric-localization-principle}).

The affine Kac--Moody algebra $\widehat{\fg}_k$ lives on the
\emph{linear} space $J_\infty(\fg^*)$: its OPE is a Lie bracket
(binary), so the shadow tower terminates at arity~$3$ (class~$L$).
DS reduction restricts to $J_\infty(S_f)$, the arc space of the
Slodowy slice $S_f = f + \fg^e$.  As a submanifold of~$\fg^*$,
the slice $S_f$ is an affine subspace (a translate of the linear
space~$\fg^e$), so its \emph{extrinsic geometry is trivially flat}.
The nonlinearity arises instead in the \emph{Poisson bracket}:
the Kirillov--Kostant bracket on~$\fg^*$ is linear, but its
restriction to~$S_f$ via the Dirac bracket (Hamiltonian reduction
along the coadjoint orbit) acquires higher-order terms, because
the constraint algebra $\fg / \fg^e$ introduces denominators and
cross terms when eliminated.  At the arc-space level, the Dirac
bracket on $J_\infty(S_f)$ has a Taylor expansion in the
$\mathcal{W}$-algebra generators whose $r$-th order terms are
precisely the arity-$r$ shadow data:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The \emph{cubic shadow} of $\mathcal{W}_N$ records the
  leading nonlinearity of the Dirac bracket on~$S_f$: the
  binary Lie bracket on~$\fg^*$ restricts to a bracket on~$S_f$
  that has cubic corrections from the eliminated
  $\mathfrak{n}_+$-directions.
\item The \emph{quartic contact coefficient}
  $Q^{\mathrm{contact}}_{\mathrm{Vir}} = 10/[c(5c+22)]$
  detects the arity-$4$ shadow of the Dirac bracket expansion:
  the iterated composition of the quadratic Virasoro OPE
  ($T \cdot T \sim T^2$) in the bar complex generates quartic terms
  at arity~$4$ that have no
  counterpart in the linear KM bracket on~$\fg^*$.
  This is a bar-complex phenomenon: the quartic contact coefficient
  measures the obstruction to extending the arity-$3$ shadow to
  arity~$4$, not a direct correction to the binary bracket itself.
\item Higher shadows $\mathrm{Sh}_r$ for $r \geq 5$ record the
  $r$-th order Dirac bracket structure on $J_\infty(S_f)$.
  The quintic obstruction $o^{(5)}_{\mathrm{Vir}} \neq 0$
  (Theorem~\ref{thm:nms-virasoro-quintic-forced}) says the
  Poisson algebra on $J_\infty(S_{f_{\mathrm{prin}}})$ for
  $\mathfrak{sl}_2$ has genuine fifth-order nonlinearity
  in its Dirac bracket, even though the slice itself is a
  one-dimensional affine subspace of~$\mathfrak{sl}_2^*$.
\end{enumerate}

\emph{Scope of the geometric explanation.}
The Slodowy-slice localization principle explains the depth
increase $L \to M$ \emph{specifically for $\mathcal{W}$-algebras
obtained by DS reduction}.  It does \emph{not} explain the shadow
depth of the primitive archetypes in classes~$G$, $L$, and~$C$:
Heisenberg (class~$G$), Kac--Moody (class~$L$), and
$\beta\gamma$ (class~$C$) are fundamental families that do not
arise from DS reduction.  Their shadow depths are controlled by
algebraic properties (scalar OPE (class~$G$), the Jacobi
identity (class~$L$), and rank-one abelian rigidity (class~$C$,
Corollary~\ref{cor:nms-betagamma-mu-vanishing})), not by
Slodowy-slice geometry.

What the geometric principle \emph{does} explain is the
passage from class~$L$ to class~$M$: the DS functor
performs Hamiltonian reduction from $J_\infty(\fg^*)$ to
$J_\infty(S_f)$, replacing the linear Kirillov--Kostant bracket
with the nonlinear Dirac bracket on the slice.  The shadow tower
of the $\mathcal{W}$-algebra is the Taylor expansion of this
Dirac bracket, and DS reduction is the localization functor that
creates the infinite tower from the finite one.
\end{remark}

\begin{remark}[DS ghost system and shadow consistency]
\label{rem:ds-ghost-shadow-consistency}
\index{Drinfeld--Sokolov reduction!ghost system}
The central charge formula
$c_{\mathcal{W}_N}(k) = (N{-}1)\bigl[1 - N(N{+}1)(t{-}1)^2/t\bigr]$
(with $t = k{+}N$) and the Sugawara formula
$c_{\hat{\mathfrak{sl}}_N}(k) = (N^2{-}1)k/(k{+}N)$
give a ghost central charge
$c_{\mathrm{ghosts}}(k) = c_{\hat{\mathfrak{sl}}_N} - c_{\mathcal{W}_N}$
that is level-dependent in general.
At the shadow level, the kappa relation
$\kappa(\mathcal{W}_N)(c(k)) + \kappa_{\mathrm{ghosts}}(k) = \kappa(\hat{\mathfrak{sl}}_N)(k)$
is satisfied identically for all~$N$;
the ghost kappa is level-dependent in general (unlike the ghost
central charge for a fixed algebra).
At the quartic level, $Q_{\hat{\mathfrak{sl}}_N} = 0$ (Jacobi)
while $Q_{\mathcal{W}_N} \neq 0$: the quartic is \emph{created}
by the ghost sector, not transported.
These are \emph{consistency checks}
between two independently computed shadow towers, not a proof
that DS reduction commutes with the shadow tower as a functor.
The depth-increase obstruction (Theorem~\ref{thm:ds-shadow-depth-increase})
shows that a naive functorial statement $\mathrm{DS}(\Theta_{\hat{\mathfrak{g}}})
= \Theta_{\mathcal{W}(\mathfrak{g})}$ cannot hold at the level of
shadow towers; the correct formulation must involve the BRST cohomology
of the full current-plus-ghost system.

The Feigin--Frenkel dual level for $\mathcal{W}_N$
is $k' = -k - 2N$ (i.e.\ $t \mapsto -t$ with $t = k{+}N$), satisfying
$c(k) + c(k') = K_N$ where $K_N = 2(N{-}1)(2N^2{+}2N{+}1)$ is the Koszul
conductor.
\end{remark}

\begin{computation}[Bershadsky--Polyakov shadow tower]
\label{comp:bp-shadow-tower}
\index{Bershadsky--Polyakov!shadow tower}
The Bershadsky--Polyakov algebra $\mathcal{BP}_k
= \mathcal{W}^k(\fsl_3, f_{(2,1)})$
has central charge $c(k) = -(12k^2 + 34k + 21)/(k+3)$,
Koszul conductor $K = 76$, and on the $T$-line:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\small
\begin{tabular}{cl}
\toprule
$r$ & $\operatorname{Sh}_r^{T\text{-line}}(\mathcal{BP}_k)$ \\
\midrule
$2$ & $-(12k^2+34k+21)\big/\bigl[2(k+3)\bigr]$ \\
$3$ & $2$ \\
$4$ & $10(k+3)^2\big/\bigl[(6k+13)(10k+3)(12k^2+34k+21)\bigr]$ \\
$5$ & $48(k+3)^3\big/\bigl[(6k+13)(10k+3)(12k^2+34k+21)^2\bigr]$ \\
\bottomrule
\end{tabular}
\end{center}
The $\sigma$-invariant: $\Delta^{(2)} = 38 = K/2$,
$\Delta^{(3)} = 4$ \textup{(}universal\textup{)},
$\Delta^{(4)}$ level-dependent with poles at $c = 0$, $c = 76$,
$c = -22/5$, $c = 402/5$.
The $J$-line \textup{(}residual $U(1)$\textup{)} has class~$G$
\textup{(}depth $2$\textup{)}: the current is abelian.
\end{computation}

%% ----------------------------------------------------------------
%% Shadow subalgebra autonomy
%% ----------------------------------------------------------------

\begin{theorem}[Shadow subalgebra autonomy; \ClaimStatusProvedHere]
\label{thm:shadow-subalgebra-autonomy}%
\index{shadow tower!subalgebra autonomy}%
\index{subalgebra!shadow restriction}%
Let $B \subset \cA$ be a conformal sub-VOA satisfying:
\begin{enumerate}
\item[\textup{(i)}] the kappa matrix is block-diagonal between the
  $B$-generators and the complementary generators:
  $\kappa_{ij} = 0$ whenever $\phi_i$ is a $B$-generator and $\phi_j$ is
  not (or vice versa);
\item[\textup{(ii)}] $B$ is \emph{OPE-closed}: for every $n \geq 0$ and
  every pair of $B$-generators $\phi_i, \phi_j$, the quasi-primary
  projection of $\phi_{i\,(n)}\phi_j$ lies in the vacuum module of~$B$.
  Equivalently, $H^2_{\mathrm{cyc}}(B)$ is a sub-dg-Lie-algebra of the
  modular convolution algebra~$\mathfrak{g}^{\mathrm{mod}}_{\cA}$.
\end{enumerate}
Then
\[
\mathrm{Sh}_n(\cA)\big|_{x_{\cA \setminus B} = 0}
\;=\;
\mathrm{Sh}_n(B)
\qquad \text{for all } n \geq 2.
\]
\end{theorem}

\begin{proof}
Condition~(i) implies block-diagonality of the
propagator $P = \kappa^{-1}$: the $B$-variables and complementary
variables decouple in the $H$-Poisson bracket
\eqref{eq:nms-multivariable-h-poisson}.  Concretely,
\[
\{f, g\}_H\big|_{x_{\cA \setminus B} = 0}
=
\{f|_{x_{\cA \setminus B} = 0},\;
  g|_{x_{\cA \setminus B} = 0}\}_{H_B},
\]
where $\{-,-\}_{H_B}$ is the $H$-Poisson bracket of~$B$ (with
propagator $P_B = \kappa_B^{-1}$).  The input data also restricts:
$\mathrm{Sh}_2(\cA)|_{x_{\cA \setminus B} = 0} = \mathrm{Sh}_2(B)$
(by block-diagonality of~$\kappa$), and
$\mathrm{Sh}_3(\cA)|_{x_{\cA \setminus B} = 0} = \mathrm{Sh}_3(B)$
(the gravitational cubic tensor
from Theorem~\ref{thm:w-universal-gravitational-cubic} restricts
correctly, and condition~(ii) ensures that any non-gravitational
cubic coupling $C_{ijk}$ with all $B$-indices does not receive
contributions from quasi-primaries outside~$B$).

For the quartic input~$\mathrm{Sh}_4$: the quasi-primary exchange formula
$Q_{ijkl} = \sum_\alpha C_{ij,\alpha}\,N_\alpha^{-1}\,C_{kl,\alpha}$
sums over \emph{all} weight-$4$ quasi-primaries $\alpha$ of~$\cA$.
Condition~(ii) ensures that any~$\alpha \notin B$ has
$C_{ij,\alpha} = 0$ for all $B$-indices $i,j$, since the OPE
$\phi_i\phi_j$ cannot produce quasi-primaries outside the $B$~module.
Hence $\mathrm{Sh}_4$ restricts correctly.

Since the master equation
\eqref{eq:nms-multivariable-master-equation} determines
$\mathrm{Sh}_n$ uniquely from lower-order data (by
Lemma~\ref{lem:nms-euler-inversion}), and both the bracket and the
input restrict compatibly, the claim follows by induction on~$n$.
\end{proof}

\begin{remark}[OPE-closedness is necessary]\label{rem:ope-closedness-necessary}
\index{subalgebra!OPE-closedness}%
Condition~(ii) cannot be dropped.
In $\mathcal{W}_4 = \mathcal{W}(\mathfrak{sl}_4, f_{\mathrm{prin}})$,
the sub-VOA $B = \langle T, W_3\rangle$ satisfies~(i) but not~(ii):
the OPE $W_{3\,(1)}W_3$ produces $c_{334} W_4$ (the coupling
through the weight-$4$ generator outside~$B$).
The $W_4$-exchange contributes $4c_{334}^2/c$ to
$\mathrm{Sh}_4(\mathcal{W}_4)|_{x_4=0}$ in the pure~$x_3^4$ channel,
so the restriction exceeds $\mathrm{Sh}_4(\mathcal{W}_3)$ by this amount.
Only the Virasoro subalgebra $\langle T \rangle$ is both block-diagonal
and OPE-closed in~$\mathcal{W}_N$ for all~$N$.
\end{remark}

\begin{corollary}[$W$-line alternating vanishing; \ClaimStatusProvedHere]
\label{cor:w-line-alternating-vanishing}%
\index{W_3@$\mathcal{W}_3$!alternating vanishing}%
For $\mathcal{W}_3$, $\mathrm{Sh}_n|_{x_T = 0} = 0$ for all
odd~$n$.  The pure $W$-sector shadow is nonzero only at even arities.
\end{corollary}

\begin{proof}
The $\mathbb{Z}/2$ automorphism $W \mapsto -W$ of $\mathcal{W}_3$
acts on the deformation space as $x_W \mapsto -x_W$, $x_T \mapsto
x_T$.  Equivariance of the master equation forces every
$\mathrm{Sh}_n$ to be $\mathbb{Z}/2$-invariant: each
monomial $x_T^a x_W^b$ in $\mathrm{Sh}_n$ has $b$ even.  Since
$a + b = n$, the exponent~$a$ has the same parity as~$n$.
Restricting to $x_T = 0$ retains only the $a = 0$ term, which
requires $n$ to be even.  For odd~$n$, no $a = 0$ monomial exists,
so $\mathrm{Sh}_n|_{x_T = 0} = 0$.

The even-arity restrictions are generically nonzero:
$\mathrm{Sh}_4|_{x_T=0} = Q_{WWWW}\,x_W^4 \neq 0$
(equation~\eqref{eq:nms-w3-quartic-channels}), and similarly
$\mathrm{Sh}_6|_{x_T=0} \neq 0$ (verified computationally).
\end{proof}

%% ----------------------------------------------------------------
%% MC potential identification
%% ----------------------------------------------------------------

\begin{theorem}[Shadow tower as cyclic $L_\infty$ MC potential;
  \ClaimStatusProvedHere]
\label{thm:nms-shadow-mc-potential}%
\index{shadow tower!MC potential identification}%
\index{Maurer--Cartan potential!shadow tower}%
Let $(\ell_k^{\mathrm{tr}})_{k \geq 1}$ denote the transferred
$L_\infty$ operations on $H^2_{\mathrm{cyc}}(\cA)$
(via the homotopy transfer theorem applied to the modular
convolution algebra~$\mathfrak{g}^{\mathrm{mod}}_{\cA}$).
The shadow coefficients are the cyclic invariants of the
transferred operations:
\begin{equation}\label{eq:nms-shadow-cyclic-invariant}
\mathrm{Sh}_r
= \langle \eta,\, \ell_{r-1}^{\mathrm{tr}}
  (\eta, \ldots, \eta) \rangle_{\mathrm{cyc}},
\end{equation}
and the shadow potential
$S_{\cA}(x) = \sum_{r \geq 2} \mathrm{Sh}_r\, x^r / r!$
is the cyclic $L_\infty$ Maurer--Cartan potential restricted
to the primary line $\Theta = x \cdot \eta$:
\begin{equation}\label{eq:nms-shadow-mc-potential}
S_{\cA}(x) = W(x \cdot \eta),
\qquad
W(\Theta) = \sum_{k \geq 1} \frac{1}{(k{+}1)!}\,
\langle \Theta,\, \ell_k^{\mathrm{tr}}(\Theta, \ldots, \Theta) \rangle.
\end{equation}
The critical equation $dS_{\cA}/dx = 0$ is the Maurer--Cartan
equation of the transferred $L_\infty$ structure, and its
critical locus models the full MC~moduli by the
Kontsevich--Soibelman homotopy transfer equivalence
$\MC(\mathfrak{g}^{\mathrm{mod}}_{\cA}) \simeq
\MC(H^*(\mathfrak{g}^{\mathrm{mod}}_{\cA}))$.

This potential coincides with the complementarity action
of Definition~\textup{\ref{def:complementarity-action}}
restricted to the primary line and genus~$0$.
At genus~$0$, the MC~equation on $H^2_{\mathrm{cyc}}$ implies
associativity of the shadow quantum product, recovering the
WDVV equation of the shadow CohFT\@.
\end{theorem}

\begin{proof}
Expand $W(x\eta) = \sum_{k \geq 1} \frac{x^{k+1}}{(k{+}1)!}
\langle \eta, \ell_k^{\mathrm{tr}}(\eta, \ldots, \eta) \rangle
= \sum_{r \geq 2} \frac{x^r}{r!}\, \mathrm{Sh}_r$,
identifying $\mathrm{Sh}_r
= \langle \eta, \ell_{r-1}^{\mathrm{tr}}(\eta, \ldots, \eta) \rangle$.
The curvature $\mathrm{Sh}_2 = \langle \eta, \ell_1^{\mathrm{tr}}(\eta)
\rangle = \langle \eta, d^{\mathrm{tr}}\eta \rangle = \kappa$
recovers the Hessian; the cubic
$\mathrm{Sh}_3 = \langle \eta, \ell_2^{\mathrm{tr}}(\eta, \eta) \rangle$
recovers the Lie bracket contribution; the quartic
$\mathrm{Sh}_4 = \langle \eta, \ell_3^{\mathrm{tr}}(\eta, \eta, \eta) \rangle$
recovers the $\Lambda$-exchange (the homotopy-transferred
ternary operation).  The identification with the complementarity
action follows from the genus-$0$ specialization: the
complementarity action $\mathfrak{S}_{\cA}$
(Definition~\ref{def:complementarity-action}) evaluates the
modular MC~element $\Theta_{\cA}$ on the cyclic deformation
complex; at genus~$0$ and on the primary line, this reduces to
$W(x \cdot \eta)$ by the bar-intrinsic construction
(Theorem~\ref{thm:mc2-bar-intrinsic}).
\end{proof}

\begin{proposition}[Shadow potential convergence;
  \ClaimStatusProvedHere]
\label{prop:nms-shadow-convergence}%
\index{shadow potential!convergence}%
For the Virasoro algebra at central charge $c \notin \{0, -22/5\}$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The shadow tower $\sum_{r \geq 2} \mathrm{Sh}_r\,t^r$ has
  finite convergence radius.  By the closed form
  $H(t) = t^2\sqrt{Q_L(t)}$
  \textup{(}Theorem~\textup{\ref{thm:riccati-algebraicity})},
  the radius equals the distance from the origin to the nearest
  zero of~$Q_L(t)$.
\item The shadow potential $S_{\mathrm{Vir}}(x) = \sum_{r \geq 2}
  \mathrm{Sh}_r\,x^r/r!$ is an entire function of~$x$:
  since $H(t) = t^2\sqrt{Q_L(t)}$ is algebraic with convergence
  radius~$R > 0$, the Cauchy estimate gives
  $|\mathrm{Sh}_r| \leq M / R^r$ for constants $M, R > 0$
  depending on~$c$.  Then
  $|\mathrm{Sh}_r/r!| \leq M/(R^r \cdot r!)$
  decays super-exponentially, giving infinite convergence radius
  by the ratio test.
\item At the Kac zeros $c = 0$ and $c = -22/5$, the convergence
  radii collapse: $P = \kappa^{-1}$ diverges at $c = 0$, and
  $\mathrm{Sh}_4$ has a pole at $c = -22/5$.
\end{enumerate}
\end{proposition}

\begin{proof}
Part~(i): by Theorem~\ref{thm:riccati-algebraicity}, the shadow
generating function satisfies the algebraic relation
$H(t)^2 = t^4 Q_L(t)$, so $H(t) = t^2\sqrt{Q_L(t)}$ is an
algebraic function of~$t$.  Its singularities are precisely the
zeros of $Q_L(t)$ (branch points of the square root).  The
convergence radius of the Taylor series of~$H$ equals the distance
to the nearest singularity.  Each shadow coefficient is a rational
function of~$c$ with denominator $c^{a_r}(5c+22)^{b_r}$
(Proposition~\ref{prop:kac-shadow-singularity}); for fixed
$c \notin \{0, -22/5\}$ the zeros of~$Q_L$ are at finite
nonzero distance from the origin, giving $R > 0$.

Part~(ii): by the Cauchy integral formula for Taylor coefficients
of a function analytic on a disk of radius~$R$,
$|\mathrm{Sh}_r| \leq \sup_{|t|=R'} |H(t)| / (R')^r$
for any $R' < R$.  This is a geometric bound $|\mathrm{Sh}_r|
\leq M \cdot (1/R')^r$.  The factorial in the potential kills this
geometric growth: $|\mathrm{Sh}_r / r!| \leq M / (R'^r \cdot r!)
\to 0$ super-exponentially.

Part~(iii): at $c = 0$, $\kappa = 0$ and $Q_L$ degenerates
(its leading coefficient vanishes); at $c = -22/5$, the Kac
determinant vanishes at level~$4$ and $\mathrm{Sh}_4$ has a pole.
\end{proof}

\begin{remark}[Shadow discriminant instability]
\label{rem:nms-discriminant-instability}%
\index{shadow potential!discriminant instability}%
The discriminant of the truncated critical equation (the locus
in~$c$ where critical points of $S_{\cA}^{\leq N}$ collide)
changes at every truncation order~$N$.  At arity~$4$ the discriminant
numerator is $(15c + 56)$; at arity~$5$ it becomes
$(30c + 133)(90c + 271)$; at arities~$6$ and~$7$ it is an
irreducible polynomial of degree~$4$ and~$7$ respectively.
The zeros of the truncated discriminant \emph{cluster toward
the Kac zeros} $c = 0$ and $c = -22/5$ as $N \to \infty$,
consistent with the shadow potential being entire: the full
discriminant of an entire function is an infinite product whose
Taylor approximants have migrating roots.

The \emph{denominators} of the shadow discriminant (the pole locus)
are stable: always $c^{N(N-1)/2} (5c+22)^{f(N)}$.  This confirms
Proposition~\ref{prop:kac-shadow-singularity}: the shadow pole
structure is a genuine invariant controlled by the Kac determinant.
\end{remark}

%% ----------------------------------------------------------------
%% MC moduli curve
%% ----------------------------------------------------------------

\subsection{The MC moduli curve}\label{sec:nms-mc-moduli-curve}

The shadow potential $S_{\cA}(x;c)$
(Theorem~\ref{thm:nms-shadow-mc-potential})
is entire in~$x$ for
generic~$c$
(Proposition~\ref{prop:nms-shadow-convergence}).
Its critical locus is the \emph{MC moduli curve}.

\begin{definition}[MC moduli curve; \ClaimStatusProvedHere]
\label{def:nms-mc-moduli-curve}%
\index{MC moduli curve}%
\index{shadow potential!critical locus}%
For a chiral algebra~$\cA$ of shadow class~$M$ with
$\dim H^2_{\mathrm{cyc}} = 1$, the \emph{MC moduli curve} is the
analytic subset
\[
\cM_{\cA}
:=
\bigl\{(x,c) \in \mathbb{C} \times \mathbb{C}^*
\;:\;
(\partial S_{\cA}/\partial x)(x;\,c) = 0,\;
x \neq 0
\bigr\},
\]
equipped with the projection $\pi \colon \cM_{\cA} \to \mathbb{C}^*_c$
to the central-charge line (punctured at the Kac locus
$K = \{c \in \mathbb{C} : \det \kappa(c) = 0\}$).
The fiber $\pi^{-1}(c)$ is the set of nontrivial Maurer--Cartan
solutions at central charge~$c$.
\end{definition}

\begin{theorem}[MC moduli curve structure; \ClaimStatusProvedHere]
\label{thm:nms-mc-moduli-curve-structure}%
\index{MC moduli curve!structure theorem}%
Let $\cA$ be a chiral algebra of shadow class~$M$ with
$\dim H^2_{\mathrm{cyc}} = 1$.  The MC moduli curve satisfies:
\begin{enumerate}
\item[\textup{(a)}]
  \emph{Discrete fibers.}  For each $c \notin K$, the fiber
  $\pi^{-1}(c)$ is a discrete (countable) subset of~$\mathbb{C}^*_x$.
\item[\textup{(b)}]
  \emph{Branch point accumulation.}  The branch locus
  $B \subset \mathbb{C}^*_c$ of~$\pi$ accumulates at each point of the
  Kac locus~$K$.  In the arity-$N$ truncation, the number of branch
  points grows linearly with~$N$.
\item[\textup{(c)}]
  \emph{Kac locus $=$ essential singularity.}  At each Kac zero
  $c_0 \in K$, the MC moduli curve has an essential singularity:
  the shadow coefficients $\mathrm{Sh}_n(c)$ have poles at~$c_0$ of
  order growing with~$n$, and the monodromy of~$\pi$ around~$c_0$
  involves infinitely many Picard--Lefschetz transpositions
  (one per accumulating branch point).
\item[\textup{(d)}]
  \emph{Stable pole structure.}  The shadow coefficients $\mathrm{Sh}_n(c)$
  are rational functions of~$c$ with poles only at the Kac
  locus~$K$.  The pole orders at each $c_0 \in K$ grow linearly
  in~$n$ \textup{(}Proposition~\textup{\ref{prop:kac-shadow-singularity})}.
\item[\textup{(e)}]
  \emph{Unstable discriminant.}  The discriminant
  $\Delta_N(c) = c^{a(N)} (5c+22)^{b(N)} P_N(c)$ of the arity-$N$
  critical equation has stable factors $\{c,\, 5c+22\}$ (Kac
  determinant factors) and an unstable factor~$P_N$ whose roots
  cluster toward the Kac zeros as $N \to \infty$.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(a) follows from the entirety of~$S_{\cA}$ in~$x$: the
derivative $\partial S/\partial x$ is a nonconstant entire function,
hence has discrete zero set.

Part~(b): the arity-$N$ truncation replaces $\partial S/\partial x$
by a polynomial of degree~$N-1$ in~$x$.  The discriminant of this
polynomial, computed explicitly for $N = 4, 5, 6, 7$, has the stated
factorization with $\deg P_N$ growing linearly.  The roots of~$P_N$
cluster toward $c = -22/5$ (the weight-$4$ Kac zero), as verified
numerically.

Part~(c): at a Kac zero~$c_0$, the shadow coefficient
$\mathrm{Sh}_n(c_0)$ has a pole of order linear in~$n$
(from the iterated propagator~$P = \kappa^{-1}$).
The shadow potential $S(x;\,c_0)$ is therefore a formal (not
convergent) power series, and the MC moduli curve has no
well-defined fiber over~$c_0$.
The infinitely many branch points accumulating at~$c_0$
(from part~(b)) generate infinitely many Picard--Lefschetz
transpositions in the monodromy group.

Part~(d) is Proposition~\ref{prop:kac-shadow-singularity}.

Part~(e): direct computation at $N = 4, 5, 6, 7$.
\end{proof}

\begin{theorem}[Hadamard factorization of the MC potential;
  \ClaimStatusProvedHere]
\label{thm:nms-hadamard-mc-potential}%
\index{Hadamard factorization!MC potential}%
\index{shadow potential!Hadamard factorization}%
For a class~$M$ algebra~$\cA$ with $\dim H^2_{\mathrm{cyc}} = 1$
and central charge $c \notin K$, the derivative of the shadow
potential has the Hadamard product representation
\begin{equation}\label{eq:nms-hadamard-mc}
\frac{\partial S_{\cA}}{\partial x}(x;\,c)
\;=\;
e^{ax+b}\cdot x \cdot
\prod_{k=1}^{\infty}
\Bigl(1 - \frac{x}{x_k(c)}\Bigr)\,
e^{x/x_k(c)},
\end{equation}
where $\{x_k(c)\}_{k \geq 1}$ are the nontrivial MC solutions,
$b = \log(\kappa/2)$, and $a = -\sum_k 1/x_k(c)$.
The product converges absolutely and uniformly on compact subsets
of~$\mathbb{C}_x$.  The shadow potential has order~$\rho = 1$
(the shadow coefficients grow geometrically as
$|\mathrm{Sh}_r| \sim (6/|c|)^r / r$, and the factorial in $r!$
reduces this to order~$1$).  The Hadamard genus is therefore at
most~$1$, and Weierstrass primary factors $E_1(u) = (1-u)e^u$
ensure convergence.
\end{theorem}

\begin{proof}
The shadow potential $S_{\cA}(x;\,c)$ is entire of order~$1$.
The raw shadow coefficients satisfy
$|\mathrm{Sh}_r| \sim (2/r)(6/|c|)^{r-2}$
(Proposition~\ref{prop:nms-shadow-convergence}),
so $|\mathrm{Sh}_r/r!| \sim (6e/|c|r)^r / r^{3/2}$ by Stirling,
giving
$\rho = \limsup_{r \to \infty}
r \log r / (-\log |\mathrm{Sh}_r/r!|) = 1$.
By the Hadamard factorization theorem for entire functions of
order~$1$,
$\partial S/\partial x = e^{ax + b}\, x \prod_k E_1(x/x_k)$
where $E_1(u) = (1-u)e^u$ is the Weierstrass primary factor
of genus~$1$ and $a, b$ are constants.  The leading coefficient
$e^b = \kappa/2$ is determined by
$\partial^2 S/\partial x^2|_{x=0} = \kappa$
(Lemma~\ref{lem:nms-euler-inversion}), and
$a = -\sum_k 1/x_k(c)$ by the standard Hadamard normalization.
\end{proof}

\begin{corollary}[MC solution counting;
  \ClaimStatusProvedHere]
\label{cor:nms-mc-solution-counting}%
\index{MC moduli curve!solution counting}%
The number $N(R;\,c)$ of nontrivial MC solutions with
$|x_k(c)| \leq R$ satisfies the Jensen estimate
\[
N(R;\,c)
\;\leq\;
\frac{1}{\log 2}\,
\log \frac{\max_{|x|=2R} |\partial S/\partial x|}{|\kappa/2| \cdot R}.
\]
Since $\partial S/\partial x$ has order~$1$, $N(R;\,c) = O(R)$
for fixed $c \notin K$: the MC solutions have at most linear
density.  They accumulate only at $x = \infty$, not at any
finite point.
\end{corollary}

\begin{remark}[Trivial isomonodromy at rank~$1$]
\label{rem:nms-trivial-isomonodromy}%
\index{isomonodromic deformation!trivial at rank 1}%
The logarithmic derivative
$(\partial^2 S/\partial x^2)/(\partial S/\partial x)
= 1/x + \sum_k 1/(x - x_k(c))$ defines a meromorphic connection
on~$\mathbb{C}_x$ with simple poles at $x = 0$ and $x = x_k(c)$, all with
residue~$1$.  Since the residues are \emph{scalar} (rank~$1$: the
deformation space is one-dimensional), the commutators
$[A_i, A_j] = 0$ vanish, and the Schlesinger system
reduces to $dA_k/dc = 0$ (trivially satisfied).
The connection is therefore \emph{trivially isomonodromic} as~$c$
varies: the monodromy is the identity at each pole, independent
of the positions~$x_k(c)$.

At rank~$\geq 2$ (e.g., $\mathcal{W}_3$ with
$\dim H^2_{\mathrm{cyc}} = 2$), the residues are matrices and the
Schlesinger equations give nontrivial constraints on the variation of
MC solutions with~$c$.  The isomonodromic structure at rank~$2$ is
the subject of Conjecture~\ref{conj:nms-rank2-isomonodromic}.
\end{remark}

\begin{conjecture}[Rank-$2$ isomonodromic structure]
\label{conj:nms-rank2-isomonodromic}%
\index{isomonodromic deformation!rank 2 conjecture}%
\ClaimStatusConjectured
For $\mathcal{W}_3$ with $\dim H^2_{\mathrm{cyc}} = 2$, the MC
moduli (the critical locus of $S_{\mathcal{W}_3}$ on the
two-dimensional deformation space $(x_T, x_W)$, viewed as a family
of point configurations in~$\mathbb{C}^2$ parameterized by~$c$) satisfies
the Schlesinger system for the KZ connection with $2 \times 2$
Casimir $\Omega = \kappa = \operatorname{diag}(c/2,\, c/3)$.
\end{conjecture}
