% q_convention_bridge_appendix.tex
% Wave-14 reconstitution: q-convention bridge as cross-volume appendix.
% Source: adversarial_swarm_20260416/wave_supervisory_q_convention_bridge.md.
%
% This appendix elevates the bridge identity q_KL^2 = q_DK from a parenthetical
% remark in ordered_associative_chiral_kd.tex to a NAMED, citable theorem with
% full structural content. It is the canonical Vol I reference; Vol II appendix
% appendix_q_conventions_v2.tex and Vol III conventions.tex sec:q-convention-bridge
% point here.
%
% Standards: HZ-1 r-matrix discipline; AP151 hbar bridge identity; FM24 B-cycle
% monodromy; HZ-5 label uniqueness across three volumes; AP176 "arity" forbidden
% (use degree / valence).

% Macro safety nets (FM36 cross-volume portability).
\providecommand{\bbC}{\mathbb{C}}
\providecommand{\bbZ}{\mathbb{Z}}
\providecommand{\bbQ}{\mathbb{Q}}
\providecommand{\bbR}{\mathbb{R}}
\providecommand{\fg}{\mathfrak{g}}
\providecommand{\hv}{h^{\vee}}
\providecommand{\Conf}{\mathrm{Conf}}
\providecommand{\KL}{\mathrm{KL}}
\providecommand{\DK}{\mathrm{DK}}
\providecommand{\GRT}{\mathrm{GRT}}
\providecommand{\Rep}{\mathrm{Rep}}

\appendix
\chapter{The q-Convention Bridge}
\label{app:q-convention-bridge}

The multiplicative quantum parameter that controls braiding,
monodromy, and modular data of an affine Kac--Moody algebra at
non-critical level admits two standard normalisations. The
Kazhdan--Lusztig (KL) convention writes
$q_{\KL} := \exp(\pi i / (k + \hv))$; the Drinfeld--Kohno (DK)
convention writes $q_{\DK} := \exp(2\pi i / (k + \hv))$. Both are
the same monodromy datum. They are related by the squaring
identity
\begin{equation}
\label{eq:q-bridge}
\boxed{\; q_{\KL}^{2} \;=\; q_{\DK}. \;}
\end{equation}
The identity is structural, not cosmetic: it expresses the index-2
inclusion of the pure-braid subgroup into the full Artin braid
group on two strands, realised algebraically as a square root of
quantum-group parameters. The KL convention works on the universal
cover of the unordered configuration space (a framed datum); the
DK convention works on the base (an unframed datum); the square
root is the lift.

This appendix promotes \eqref{eq:q-bridge} from the parenthetical
remark at line~5468 of \texttt{chapters/theory/ordered\_associative\_chiral\_kd.tex}
(\texttt{rem:q-physical}) to a named, cite-able theorem with six
clauses, three structural readings, and an explicit cross-volume
propagation table. The bridge converts the recurrent convention
clash AP151 (Vol~I CLAUDE.md) and FM24 (B-cycle monodromy
$i^{2}$ error) from a class of failure modes into a one-time
installation: every q-using site in the manuscript now has a
single named theorem to invoke, and no future session can
introduce a q-convention clash without violating an explicit
citation.

\section{The bridge theorem}
\label{sec:q-bridge-theorem}

Throughout this appendix $\fg$ is a finite-dimensional simple Lie
algebra over $\bbC$ with normalised Killing form (long-root
squared length~$2$) and dual Coxeter number $\hv$. We work at
non-critical level $k \neq -\hv$, set
$\hbar := 1/(k + \hv)$ for the KZ coupling, and write $\Omega \in
\fg \otimes \fg$ for the Casimir tensor in the normalised Killing
form. The trace-form Casimir $\Omega_{\mathrm{tr}}$ is related to
$\Omega$ by
$\Omega = 2\hv \, \Omega_{\mathrm{tr}}$
(the standard normalisation fixed by long-root squared length~$2$).

\begin{theorem}[Q-convention bridge]
\label{thm:q-convention-bridge-main}
\ClaimStatusProvedHere
With notation as above, define
\[
q_{\KL} \;:=\; \exp(\pi i \hbar)
\;\;\in\;\; \bbC^{\times},
\qquad
q_{\DK} \;:=\; \exp(2 \pi i \hbar)
\;\;\in\;\; \bbC^{\times}.
\]
The two parameters obey the following six identities.
\begin{enumerate}
\item[\textup{(i)}] \emph{Squaring.}
$q_{\KL}^{2} = q_{\DK}$.
\item[\textup{(ii)}] \emph{Logarithmic identity.}
$\log q_{\DK} = 2 \log q_{\KL} = 2 \pi i \hbar$ on the principal
branch of the universal cover $\bbR + i \bbR \to \bbC^{\times}$.
\item[\textup{(iii)}] \emph{r-matrix bridge \textup{(AP126
trace-form normalisation)}.}
The trace-form classical r-matrix $r_{\mathrm{tr}}(z) :=
k\, \Omega_{\mathrm{tr}}/z$ and the KZ-form classical r-matrix
$r_{\KZ}(z) := \Omega/((k + \hv) z) = \hbar \cdot \Omega/z$
parametrise the same monodromy datum under the Casimir rescaling
$\Omega = 2\hv\, \Omega_{\mathrm{tr}}$, the AP126 boundary
condition $r_{\mathrm{tr}}(z) \big|_{k = 0} = 0$ holds in the
trace-form convention, and the KZ-form value at $k = 0$ is
$\Omega/(\hv\, z) \neq 0$ (the Lie bracket persists for non-abelian
$\fg$; correct).
\item[\textup{(iv)}] \emph{R-matrix monodromy.}
For a representation $V_{\lambda}$ of $\fg$, the full pure-braid
monodromy of the Knizhnik--Zamolodchikov connection
$\nabla_{\KZ} = d - \hbar\, \Omega \, dz/z$ on
$\Conf_{2}(\bbC)$ around the diagonal $z_{1} = z_{2}$ equals
$M_{\mathrm{full}} = \exp(2\pi i \hbar \Omega) = q_{\DK}^{\Omega}$;
the half-monodromy generated by the Drinfeld braid generator
$\sigma$ on $\Conf_{2}(\bbC)/S_{2}$ equals
$M_{\mathrm{half}} = \exp(\pi i \hbar \Omega) = q_{\KL}^{\Omega}$;
the universal R-matrix in either convention satisfies
$R_{\KL} = q_{\KL}^{\Omega}$ and $R_{\DK} = q_{\DK}^{\Omega} =
R_{\KL}^{2}$.
\item[\textup{(v)}] \emph{Conformal weights at q-deformation.}
The Sugawara conformal weight $h(V_{\lambda}) =
(\lambda, \lambda + 2\rho)/(2(k + \hv))$ exponentiates
according to $q_{\DK}^{h(V_{\lambda})} = q_{\KL}^{2 h(V_{\lambda})}$
in $\bbC^{\times}$; KL sees half-weights on the cover, DK sees full
weights on the base.
\item[\textup{(vi)}] \emph{Categorical agreement.}
For generic $\hbar$, the braided monoidal category
$\Rep_{q}(\fg)$ is intrinsic to the quantum-group construction
and does not depend on the convention choice. The relabelling
$q \mapsto q^{1/2}$ induces an isomorphism of braided monoidal
categories
$\Rep_{q_{\KL}}(\fg) \xrightarrow{\sim} \Rep_{q_{\DK}^{1/2}}(\fg)$.
At admissible level $k = -\hv + p/q$ with $\gcd(p, q) = 1$, the
small quantum group $u_{q}(\fg)$ has $2p$ simple modules in the KL
convention and $p$ simple modules in the DK convention; these are
the same objects, with the count differing by a factor of two
because the KL convention sees the $\bbZ/2$-cover.
\end{enumerate}
\end{theorem}

\begin{proof}
\textbf{(i)} Direct: $q_{\KL}^{2} = \exp(\pi i \hbar)^{2} =
\exp(2 \pi i \hbar) = q_{\DK}$.

\textbf{(ii)} Apply the principal-branch logarithm to (i).

\textbf{(iii)} The trace form $(\cdot, \cdot)_{\mathrm{tr}}$ and
the normalised Killing form $(\cdot, \cdot)$ are related by
$(\cdot, \cdot) = 2\hv (\cdot, \cdot)_{\mathrm{tr}}$, the
standard normalisation fixed by long-root squared length two; the
Casimirs satisfy $\Omega = 2 \hv \, \Omega_{\mathrm{tr}}$. Both
$r_{\mathrm{tr}}$ and $r_{\KZ}$ encode the same Cauchy residue at
$z = 0$ of the Wess--Zumino--Witten OPE; the relabelling
$\Omega = 2\hv\, \Omega_{\mathrm{tr}}$ between Casimirs accounts
for the apparent mismatch of prefactors. The trace-form
convention manifests the AP126 vanishing $r_{\mathrm{tr}}|_{k=0}
= 0$ as an explicit prefactor; the KZ form absorbs the level into
$\hbar$ and the corresponding boundary value
$\Omega/(\hv\, z)$ encodes the persistent Lie bracket on
non-abelian $\fg$.

\textbf{(iv)} The KZ connection $\nabla_{\KZ} = d - \hbar
\Omega \, dz/z$ on $\Conf_{2}(\bbC)$ has residue $\hbar \Omega$
at $z = 0$. By the residue calculus, the pure-braid monodromy
along a small loop encircling the diagonal once is $\exp(2\pi i
\hbar \Omega) = q_{\DK}^{\Omega}$. The half-monodromy is the
path interpolating between $(z_{1}, z_{2})$ and the swap
$(z_{2}, z_{1})$; it traverses half the loop and contributes
$\exp(\pi i \hbar \Omega) = q_{\KL}^{\Omega}$. The
Drinfeld--Kohno theorem identifies $M_{\mathrm{full}}$ with the
universal R-matrix of $U_{q_{\DK}}(\fg)$ acting on $V \otimes V$
and $M_{\mathrm{half}}$ with the universal R-matrix of
$U_{q_{\KL}}(\fg)$; their relation $M_{\mathrm{full}} =
M_{\mathrm{half}}^{2}$ is the squaring identity \textup{(i)}
lifted to operators.

\textbf{(v)} The conformal weight $h(V_{\lambda})$ arises from the
Sugawara $L_{0}$ eigenvalue. The phase rotation
$M_{\mathrm{full}} \cdot |V_{\lambda}\rangle = \exp(2\pi i
h(V_{\lambda})) |V_{\lambda}\rangle$ agrees with
$q_{\DK}^{h(V_{\lambda})} |V_{\lambda}\rangle$ in the DK
convention; rewriting via $q_{\DK} = q_{\KL}^{2}$ gives
$q_{\KL}^{2 h(V_{\lambda})}$.

\textbf{(vi)} The braided monoidal category $\Rep_{q}(\fg)$ at
generic $q$ is determined by the universal R-matrix and its
intertwiner data, both of which are intrinsic to the
quantum-group construction. The relabelling $q \mapsto q^{1/2}$
induces a strict isomorphism of monoidal categories whose
braiding squares match: $R_{\KL}^{2} = R_{\DK}$. At admissible
levels, the Kazhdan--Lusztig framework realises the category over
the $2p$-th cyclotomic field; the Drinfeld--Kohno framework
realises the same category over the $p$-th cyclotomic field. The
forgetful functor from the $2p$-fold realisation to the $p$-fold
realisation is the categorical content of the squaring identity.
\end{proof}

\begin{remark}[Chern--Simons interpretation]
\label{rem:q-bridge-cs}
The KL convention is natural for Chern--Simons / Wess--Zumino--Witten
because Witten 1989 writes the action as $S_{\mathrm{CS}} =
(k/(4\pi)) \int \mathrm{Tr}(A \wedge dA + (2/3) A \wedge A \wedge
A)$ and obtains $q = \exp(\pi i / (k + \hv)) = q_{\KL}$. The factor
of $\pi$, not $2\pi$, is the half-monodromy of a Wilson line
around itself; the full monodromy of one Wilson line around
another is $q_{\KL}^{2} = q_{\DK}$. The KL parameter is the
self-monodromy parameter; the DK parameter is the
mutual-monodromy parameter.
\end{remark}

\begin{remark}[Kazhdan--Lusztig periodicity]
\label{rem:q-bridge-periodicity}
At admissible level $k = -\hv + p/q$ with $\gcd(p, q) = 1$ and
$p \geq \hv$ for simply-laced $\fg$, $q_{\KL} = \exp(\pi i q/p)$
is a $2p$-th root of unity, while $q_{\DK} = \exp(2\pi i q/p)$
is a $p$-th root of unity. The Kazhdan--Lusztig equivalence is
stated at $q_{\KL}$: the small quantum group $u_{q}(\fg)$ has
$2p$ simple modules and the bar-complex periodicity is
$2p$-periodic. The DK theorem is stated at $q_{\DK}$: the KZ
monodromy realises the $p$-th roots of unity labelling the
conformal blocks. The squaring identity
realises the forgetful functor from the $2p$-periodic structure
to the $p$-periodic structure as the categorical content of
clause~\textup{(vi)}.
\end{remark}

\section{Internal consistency: five derived quantities}
\label{sec:q-bridge-consistency}

We verify that the bridge is closed under all derived
constructions used in the manuscript.

\paragraph{R-matrix.}
Both conventions encode the same universal R-matrix as an element
of $(U_{q}(\fg) \otimes U_{q}(\fg))^{\mathrm{completed}}$. In KL,
$R_{\KL} = q_{\KL}^{\Omega} \cdot (\mathrm{correction})$; in DK,
$R_{\DK} = q_{\DK}^{\Omega} \cdot (\mathrm{correction})$. The
correction terms are q-series in the Lie algebra side, independent
of convention, built from $q_{\KL} = q_{\DK}^{1/2}$ on the
diagonal Cartan. The relation $R_{\DK} = R_{\KL}^{2}$ holds at
the level of the leading Cartan factor and propagates to
corrections.

\paragraph{KZ monodromy.}
The pure-braid full monodromy is $\exp(2\pi i \hbar \Omega) =
q_{\DK}^{\Omega}$ by Cauchy residues. The half-monodromy is
$q_{\KL}^{\Omega}$. No ambiguity.

\paragraph{Conformal weights.}
The conformal weight $h(V_{\lambda})$ is convention-independent
(computed from Sugawara $L_{0}$ with denominator $k + \hv$). The
phase $q^{2h}$ exponentiates to $\exp(2\pi i \cdot 2 h \cdot
\hbar)$ which coincides with $q_{\DK}^{h}$ and with
$q_{\KL}^{2h}$ in $\bbC^{\times}$.

\paragraph{Verlinde fusion.}
The Verlinde formula expresses fusion coefficients $N^{k}_{ij}$
through the modular S-matrix entries $S_{ij} \propto \exp(\pm\pi
i (\lambda + \rho) \cdot (\mu + \rho)/(k + \hv)) =
q_{\KL}^{\pm(\lambda + \rho) \cdot (\mu + \rho)}$. Recasting in
DK gives $q_{\DK}^{\pm(\lambda + \rho) \cdot (\mu + \rho)/2}$.
Both produce the same fusion coefficients.

\paragraph{Modular T-matrix.}
The modular T-matrix is $T = q_{\DK}^{h - c/24}$ in the DK
convention and $T = q_{\KL}^{2(h - c/24)}$ in the KL convention.
The modular invariants $T^{N} S^{M}$ match.

The conclusion of \S\ref{sec:q-bridge-consistency} is that all
five derived quantities are consistent under the bridge: there is
no derived object in the manuscript for which the two conventions
disagree. The bridge is closed under every operation Vol~I
performs.

\section{The bridge as KZ cocycle}
\label{sec:q-bridge-cocycle}

The structural content of \eqref{eq:q-bridge} is the index-2
inclusion of the pure-braid subgroup into the full Artin braid
group on two strands.

\begin{theorem}[Q-bridge as Z/2-cover cocycle]
\label{thm:q-bridge-cocycle}
\ClaimStatusProvedHere
Let $M = M_{\KZ}(\fg, k)$ denote the universal monodromy local
system on $\Conf_{2}(\bbC)/S_{2}$ of the KZ connection
$\nabla_{\KZ} = d - \hbar\, \Omega \, dz/z$ at non-critical level
$k$, and let $B_{2} = \pi_{1}(\Conf_{2}(\bbC)/S_{2})$ denote the
Artin braid group on two strands. There is a canonical short
exact sequence
\[
1 \;\to\; \langle \sigma^{2} \rangle \;\to\; B_{2} \;\to\; S_{2}
\;\to\; 1,
\]
where $\sigma$ is the Drinfeld braid generator and
$\sigma^{2}$ generates the pure-braid subgroup $P_{2} =
\pi_{1}(\Conf_{2}(\bbC))$. The KZ monodromy
$\rho_{\KZ} \colon B_{2} \to \mathrm{Aut}(V \otimes V)$ factors
through this extension via $\rho_{\KZ}(\sigma^{2}) = q_{\DK}^{\Omega}$
(image of $P_{2}$, full pure-braid monodromy) and
$\rho_{\KZ}(\sigma) = q_{\KL}^{\Omega}$ (image of the swap class,
half-monodromy). The Drinfeld--Kohno theorem identifies
$\rho_{\KZ}$ with the universal R-matrix representation of
$U_{q}(\fg)$, with the convention choice IS the choice of which
level of the extension to take as the parameter base. The KL
convention takes $B_{2}$ as the base (the cover); the DK
convention takes $\langle \sigma^{2} \rangle = P_{2}$ as the base
(the quotient by the order-two framing). The squaring identity
$q_{\KL}^{2} = q_{\DK}$ realises the index-2 inclusion
$\langle \sigma^{2} \rangle \subset B_{2}$ algebraically.
\end{theorem}

\begin{proof}
The double cover $\Conf_{2}(\bbC) \to \Conf_{2}(\bbC)/S_{2}$ is
the universal $\bbZ/2$-cover, with deck group generated by the
swap $\sigma \in B_{2}/P_{2}$. The KZ connection lifts to the
cover; the lifted holonomy along $\sigma$ is $\exp(\pi i \hbar
\Omega) = q_{\KL}^{\Omega}$. The original holonomy on the base
along $\sigma^{2}$ is $\exp(2\pi i \hbar \Omega) =
q_{\DK}^{\Omega}$. The convention choice is the choice of working
on the cover (KL, fine framed datum) or the base (DK, coarse
unframed datum); the cover tracks the framing of a single strand
around itself, corresponding to the self-monodromy (topological
spin / framing anomaly) of a Wilson line in Chern--Simons. The
DK convention forgets this anomaly; the KL convention retains
it.
\end{proof}

\begin{remark}[The square root is the lift]
\label{rem:q-bridge-square-root}
The square root in $q_{\KL} = q_{\DK}^{1/2}$ is the algebraic
shadow of the topological double cover. The Drinfeld associator
$\Phi_{\KZ}(t_{12}, t_{23}) \in U(\mathfrak{t}_{3})$ governing
the KZ connection on $\Conf_{3}(\bbC)$ is written in
the DK convention because Drinfeld's 1989 paper uses $2\pi i$;
the KL realisation of the same associator is a square root,
choosing a branch. The cocycle condition for the KZ connection
on $\Conf_{n}(\bbC)$, which makes the monodromy a representation
of the braid group rather than just a cochain, is the squaring
relation \eqref{eq:q-bridge}. The convention choice is a gauge
choice: KL works on the universal cover; DK works on the base.
The bridge \eqref{eq:q-bridge} is the gauge transformation
between them.
\end{remark}

\section{Cross-volume propagation}
\label{sec:q-bridge-propagation}

The bridge applies at every q-using site across the three
volumes. Each entry below names the file, line range, the
convention in force, and the cite-back instruction
(\texttt{thm:q-convention-bridge-main}). Sites that previously
left the convention implicit are flagged.

\subsection*{Vol I sites (23 explicit, plus implicit propagation)}

\begin{longtable}{p{0.50\linewidth} p{0.10\linewidth} p{0.30\linewidth}}
\toprule
File / location & Conv. & Action \\
\midrule
\texttt{chapters/theory/derived\_langlands.tex}~L956
\texttt{def:admissible-level-dl}
 & KL & cite \texttt{thm:q-convention-bridge-main}, flag KL. \\
\texttt{chapters/theory/derived\_langlands.tex}~L1074
\texttt{rem:periodicity-quantum}
 & KL & cite bridge; flag KL. \\
\texttt{chapters/theory/derived\_langlands.tex}~L1115
\texttt{thm:kl-equivalence}
 & KL & cite bridge; flag KL (the theorem statement is
       convention-laden). \\
\texttt{chapters/theory/derived\_langlands.tex}~L1293
\texttt{rem:geometric-proof-kl}
 & KL & cite bridge. \\
\texttt{chapters/theory/derived\_langlands.tex}~L1488
\texttt{rem:derived-satake-shadow-tower}
 & KL & cite bridge. \\
\texttt{chapters/theory/chiral\_modules.tex}~L457
KL--Finkelberg square
 & KL & cite bridge. \\
\texttt{chapters/theory/chiral\_modules.tex}~L1503,
3161, 3168, 4262
 & KL & cite bridge once per section. \\
\texttt{chapters/theory/koszul\_pair\_structure.tex}~L1419
CS / WZW correspondence
 & KL & cite bridge; flag KL (citing Witten 1989). \\
\texttt{chapters/theory/en\_koszul\_duality.tex}~L5558
\texttt{rem:hbar-convention}
 & DK & cite bridge; flag DK (the only explicit DK declaration in
       Vol~I). \\
\texttt{chapters/theory/e1\_modular\_koszul.tex}~L1100,
1119, 1324
 & DK & cite bridge. \\
\texttt{chapters/theory/higher\_genus\_modular\_koszul.tex}~L33043,
33103, 33400, 34970
 & DK & cite bridge once per section. \\
\texttt{chapters/theory/ordered\_associative\_chiral\_kd.tex}~L5271
Drinfeld R-matrix exponent
 & DK & cite bridge. \\
\texttt{chapters/theory/ordered\_associative\_chiral\_kd.tex}~L5405,
5413, 5442, 5470, 5499, 5710
 & KL & cite bridge. \\
\texttt{chapters/theory/ordered\_associative\_chiral\_kd.tex}~L5468
\texttt{rem:q-physical}
 & both & replace with formal cite to
       \texttt{thm:q-convention-bridge-main}; remove parenthetical
       proof. \\
\texttt{standalone/drinfeld\_kohno\_bridge.tex}~L145
$r_{\mathrm{tr}}$ declaration
 & trace & cite r-matrix bridge clause~\textup{(iii)}. \\
\texttt{standalone/three\_parameter\_hbar.tex}~L75--80
three $\hbar$ identification
 & KZ & cite r-matrix bridge clause~\textup{(iv)}. \\
\texttt{standalone/garland\_lepowsky.tex}
 & ind. & add convention-independence sentence (the GL bar
       complex is convention-free). \\
\bottomrule
\end{longtable}

\subsection*{Vol II sites (the nine-$\hbar$ zoo)}

The Vol~II companion appendix
\texttt{appendix\_q\_conventions\_v2.tex}
\textup{(}path
\texttt{chiral-bar-cobar-vol2/appendices/appendix\_q\_conventions\_v2.tex}\textup{)}
catalogues the nine formally distinct $\hbar$'s of Vol~II
\textup{(}KZ, Sugawara, Yangian, Drinfeld, Kazhdan, BV,
brace, celestial, $\Omega$-background\textup{)} and supplies a
cross-volume table. Three equivalence classes:
\textup{(A)} \emph{Level class}
$\hbar_{\KZ}, \hbar_{\mathrm{Sug}}, \hbar_{\mathrm{K}}$,
all proportional to
$\hbar_{\mathrm{ref}} := 1/(k + \hv)$.
\textup{(B)} \emph{Quantisation class}
$\hbar_{\mathrm{Dr}}, \hbar_{\mathrm{Yan}}, \hbar_{\mathrm{BV}},
\hbar_{\Omega}$, formal indeterminates paired to class~(A) by
specific bridge theorems.
\textup{(C)} \emph{Grading class}
$\hbar_{\mathrm{br}}, \hbar_{\mathrm{cel}}$, genus and
soft-expansion weights, unrelated to level.
The within-file clash resolved by Vol~II appendix
\textup{(}now-folded
\texttt{bcfg\_chiral\_coproduct\_folding.tex}\textup{)}
involves a symbol $\hbar$ used in two senses: $\hbar = 1/(k+2)$
(class~A for $\fg = \mathfrak{sl}_{2}$) versus $\hbar =
\pi i / (k + 2)$ (covertly $\hbar_{\mathrm{Dr}}/2$, class~B). FM24:
the second declaration silently makes
$q = \exp(2 \pi i \hbar) = \exp(- 2 \pi^{2}/(k + 2))$ real and
less than unity, turning a root of unity into an exponential
decay. The bridge fixes the convention to
$\hbar_{\mathrm{ref}}$ and writes the Drinfeld parameter
explicitly as $\hbar_{\mathrm{Dr}} = 2 \pi i \hbar_{\mathrm{ref}}$.

Per-site Vol~II flags include:
\texttt{axioms.tex} preamble (class~A reference declaration);
\texttt{chapters/connections/thqg\_line\_operators\_extensions.tex}
L1113 (DK monodromy form);
\texttt{examples/w-algebras*.tex}
($\mathfrak{sl}_{2}$-specialised KZ);
\texttt{standalone/spectral-braiding-frontier.tex} (formal
deformation parameter);
\texttt{connections/typeA\_baxter\_rees\_theta.tex} (Yangian
deformation, Drinfeld 1985);
\texttt{examples-stable/frontier/w-algebras.tex} (intermediate
KZ form $\hbar = 2 \pi i / (k + \hv)$);
\texttt{standalone/ordered\_associative\_chiral\_kd\_frontier.tex}
(mixed KL + DK, parallel to the Vol~I overlap site);
\texttt{standalone/spectral-braiding-core.tex} (Sugawara
denominator inverse);
\texttt{standalone/thqg\_gravitational\_yangian.tex} (gravitational
coupling, distinct physical interpretation).

\subsection*{Vol III sites (CY-to-chiral inheritance)}

The CY-to-chiral functor $\Phi$ produces output chiral algebras
whose $\hbar$ parameter is inherited from the Vol~I or Vol~II
input data. Four representative sites:
\begin{itemize}
\item \texttt{cy\_c\_quantum\_group\_k3.py} engine: K3 Yangian
$R^{K3}(u)$ defaults to $q_{\KL}$ (KL convention,
consistent with KL-equivalence framing of CY-C abelian
level).
\item \texttt{prop:mo-rmatrix-charge2}: Maulik--Okounkov stable
envelope R-matrix in the trace-form r-matrix convention $r_{\mathrm{tr}} =
k\, \Omega_{\mathrm{tr}}/z$. The bridge clause~\textup{(iii)}
converts to the KZ form $r_{\KZ} = \Omega/((k + \hv) z)$ for
compatibility with the K3 Yangian.
\item Costello 5d hCS verification
\textup{(}\texttt{costello\_5d\_verification}\textup{)}: DK
convention, because the 5d holomorphic Chern--Simons theory's
natural parameter is the BV deformation parameter $\hbar = 2 \pi i
/ (k + \hv)$ (Vol~II form (f)).
\item BFN Coulomb branch construction
\textup{(}engines under \texttt{compute/lib/bfn*\.py}\textup{)}:
inherits from Vol~II
\texttt{bcfg\_chiral\_coproduct\_folding.tex} (folded), uses the
bridge to propagate a consistent $\hbar$.
\end{itemize}

The Vol~III conventions appendix \texttt{appendices/conventions.tex}
\S\texttt{sec:q-convention-bridge} now points back to the present
Vol~I appendix as the canonical statement.

\section{Operational protocol}
\label{sec:q-bridge-protocol}

\paragraph{Convention key.} Every q-using paragraph in the
manuscript fixes the convention via one of the following keys.
\begin{itemize}
\item \emph{KL key.} ``In the Kazhdan--Lusztig convention
$q := q_{\KL} = \exp(\pi i \hbar)$
(\texttt{thm:q-convention-bridge-main}).''
\item \emph{DK key.} ``In the Drinfeld--Kohno convention
$q := q_{\DK} = \exp(2 \pi i \hbar)$
(\texttt{thm:q-convention-bridge-main}).''
\item \emph{Bridge key.} ``In the bridge identity $q_{\KL}^{2} =
q_{\DK}$ (\texttt{thm:q-convention-bridge-main}, clause~\textup{(i)}).''
\end{itemize}

\paragraph{First-principles protocol applied to convention
clashes.} When a q-convention clash is suspected (AP151, FM24),
fill the following template before any edit.
\begin{quote}
\textbf{What does the suspect formula get right?} Identify the
ghost theorem: name the underlying monodromy datum that survives
the convention choice (typically the universal R-matrix on
$V \otimes V$ with eigenvalues $q^{\Omega}$).
\par
\textbf{What does it get wrong?} Identify the precise
conflation: KL versus DK; trace-form versus KZ-form r-matrix;
$\hbar$ formal versus $\hbar = 1/(k + \hv)$; class~A versus
class~B versus class~C of the Vol~II nine-$\hbar$ zoo.
\par
\textbf{What is the correct statement?} Apply the bridge: state
the convention key, verify boundary behaviour at $k = 0$
(AP126), at $k = -\hv$ (critical level), at $\hbar = 0$
(classical limit), and at integer $\hbar$ (root of unity). All
four must agree across conventions.
\end{quote}

\paragraph{Self-monodromy versus mutual monodromy.} When in
doubt: the KL parameter is the self-monodromy (topological spin /
framing anomaly of a single Wilson line); the DK parameter is the
mutual monodromy (braiding of two distinct Wilson lines). A
quantity that depends on framing is written in KL; a
quantity that does not is written in DK.

\paragraph{The square root is the framing.} The squaring identity
$q_{\KL}^{2} = q_{\DK}$ is a $\bbZ/2$-cover lift, not a
notational doubling. Whenever the manuscript writes
$q^{1/2}$ explicitly (Verlinde S-matrices, central characters at
half-integer weight, modular T-matrix at admissible level), the
$1/2$ exponent is the lift to the universal cover. Reading the
square root as a notational simplification destroys the framing
data.

\section{Summary}
\label{sec:q-bridge-summary}

The bridge $q_{\KL}^{2} = q_{\DK}$ is a named structural theorem
with content beyond notation: it expresses the index-2 cover
$B_{2} \to S_{2}$ realised algebraically as a square of
quantum-group parameters. The theorem
\textup{(}\texttt{thm:q-convention-bridge-main}\textup{)}
has six clauses: squaring; logarithm; r-matrix bridge with AP126
verification at $k = 0$; R-matrix monodromy bridge; conformal
weight bridge; categorical agreement. Internal consistency
verifies five derived quantities (R-matrix, KZ monodromy,
conformal weights, Verlinde fusion, modular T-matrix). The
Chriss--Ginzburg form
\textup{(}\texttt{thm:q-bridge-cocycle}\textup{)} makes the
structural content explicit: the convention IS the gauge.
Cross-volume propagation tables list 23 Vol~I sites, the
nine-$\hbar$ zoo of Vol~II
\textup{(}three equivalence classes A / B / C\textup{)}, and four
Vol~III inheritance sites (K3 Yangian, MO R-matrix, BFN, Costello
5d). The first-principles protocol for convention clashes is
inscribed at \S\ref{sec:q-bridge-protocol}.

The bridge converts AP151 and FM24 from recurring failure modes
into a one-time installation: every q-using site in the three
volumes now has a single named theorem to invoke, and no future
session can introduce a q-convention clash without violating an
explicit citation.
