\chapter{Sign conventions and shifts}
\label{app:signs}

\index{sign conventions|textbf}

The sign conventions used throughout this monograph are chosen for compatibility with
Loday--Vallette~\cite{LV12} (operadic structures),
Beilinson--Drinfeld~\cite{BD04} (chiral algebras), and Lurie~\cite{HA}
($\infty$-categorical foundations).

\section{The Koszul sign rule}
\label{sec:koszul-sign-rule}

\begin{convention}[Koszul sign rule]
\label{conv:koszul}
\index{Koszul sign rule|textbf}
Let $\cC$ be a graded category (chain complexes, differential graded algebras, 
graded vector spaces, etc.). When two homogeneous elements $a$ and $b$ of 
degrees $|a|$ and $|b|$ respectively are interchanged in any formula, a sign 
$(-1)^{|a| \cdot |b|}$ must be introduced:
\[
a \otimes b \longmapsto (-1)^{|a| \cdot |b|} \, b \otimes a.
\]
This rule applies universally: to tensor products, compositions, evaluations, 
and any operation where the order of graded objects matters.
\end{convention}

\begin{definition}[Graded commutator]
\label{def:graded-commutator}
For homogeneous elements $a, b$ in a graded algebra $A$, the 
\emph{graded commutator} is:
\[
[a, b] := a \cdot b - (-1)^{|a| \cdot |b|} b \cdot a.
\]
An algebra is \emph{graded commutative} if $[a, b] = 0$ for all homogeneous 
$a, b$, which is equivalent to $a \cdot b = (-1)^{|a| \cdot |b|} b \cdot a$.
\end{definition}

\begin{proposition}[Graded Jacobi identity; \ClaimStatusProvedHere]
\label{prop:graded-jacobi}
For any graded Lie algebra $(L, [-,-])$, the bracket satisfies the 
\emph{graded Jacobi identity}:
\[
(-1)^{|a| \cdot |c|} [a, [b, c]] + (-1)^{|b| \cdot |a|} [b, [c, a]] 
+ (-1)^{|c| \cdot |b|} [c, [a, b]] = 0.
\]
This is equivalent to requiring that the adjoint action $\ad_a = [a, -]$ 
is a derivation of the bracket:
\[
[a, [b, c]] = [[a, b], c] + (-1)^{|a| \cdot |b|} [b, [a, c]].
\]
\end{proposition}

\begin{proof}
The equivalence follows from expanding the graded Jacobi identity and 
applying graded antisymmetry $[b, c] = -(-1)^{|b| \cdot |c|} [c, b]$. 
The cyclic sum becomes:
\begin{align*}
0 &= (-1)^{|a| \cdot |c|} [a, [b, c]] + (-1)^{|b| \cdot |a|} [b, [c, a]] 
 + (-1)^{|c| \cdot |b|} [c, [a, b]] \\
 &= (-1)^{|a| \cdot |c|} [a, [b, c]] 
 - (-1)^{|b| \cdot |a|} (-1)^{|a| \cdot |c|} [b, [a, c]] 
 + (-1)^{|c| \cdot |b|} [c, [a, b]] \\
 &= (-1)^{|a| \cdot |c|} \bigl( [a, [b, c]] - (-1)^{|a| \cdot |b|} [b, [a, c]] 
 - [[a, b], c] \bigr),
\end{align*}
using $[[a,b],c] = -(-1)^{(|a|+|b|)|c|}[c,[a,b]]$ and simplifying exponents.
\end{proof}

\begin{convention}[Sign in differential graded structures]
\label{conv:dg-signs}
In a differential graded algebra $(A, d, \cdot)$:
\begin{enumerate}[label=(\roman*)]
\item The differential has degree $|d| = +1$ (cohomological convention) 
or $|d| = -1$ (homological convention).
\item The Leibniz rule incorporates the Koszul sign:
\[
d(a \cdot b) = (da) \cdot b + (-1)^{|a|} a \cdot (db).
\]
\item For a differential graded Lie algebra, the bracket-differential 
compatibility is:
\[
d[a, b] = [da, b] + (-1)^{|a|} [a, db].
\]
\end{enumerate}
Throughout this monograph, we use the \emph{cohomological convention} 
$|d| = +1$ unless explicitly stated otherwise.
\end{convention}

\begin{lemma}[Sign rule for compositions \cite{LV12}; \ClaimStatusProvedElsewhere]
\label{lem:composition-signs}
Let $f: V \to W$ and $g: W \to X$ be graded linear maps of degrees $|f|$ 
and $|g|$ respectively. The composition $g \circ f: V \to X$ has degree 
$|g \circ f| = |f| + |g|$. For evaluation on $v \in V$:
\[
(g \circ f)(v) = g(f(v)) \quad \text{(no sign)}.
\]
However, when expressing $g \circ f$ in terms of tensor factors, the 
Koszul rule applies:
\[
(f \otimes g) \circ \tau_{V,W} = (-1)^{|f| \cdot |g|} \tau_{V,X} \circ (g \otimes f)
\]
where $\tau$ denotes the graded twist map.
\end{lemma}

\begin{definition}[Graded Hom complex]
\label{def:graded-hom}
For chain complexes $(V, d_V)$ and $(W, d_W)$, the \emph{internal Hom complex} 
$\underline{\Hom}(V, W)$ has:
\begin{enumerate}[label=(\roman*)]
\item Degree $n$ component: $\underline{\Hom}(V, W)^n = \prod_{k \in \bZ} 
\Hom_k(V^k, W^{k+n})$, i.e., degree-$n$ maps.
\item Differential: For $f \in \underline{\Hom}(V, W)^n$,
\[
(d_{\underline{\Hom}} f)(v) := d_W(f(v)) - (-1)^{|f|} f(d_V(v)).
\]
\end{enumerate}
The sign $(-1)^{|f|}$ ensures $d_{\underline{\Hom}}^2 = 0$.
\end{definition}

\begin{verification}[\texorpdfstring{$d_{\underline{\Hom}}^2 = 0$}{d\_Hom\textasciicircum 2 = 0}]
\label{ver:d-hom-squared}
For $f$ of degree $|f|$:
\begin{align*}
(d^2 f)(v) &= d\bigl( d_W(f(v)) - (-1)^{|f|} f(d_V v) \bigr) 
 - (-1)^{|f|+1} \bigl( d_W(f(v)) - (-1)^{|f|} f(d_V v) \bigr)|_{v \mapsto d_V v} \\
&= d_W^2(f(v)) - (-1)^{|f|} d_W(f(d_V v)) 
 - (-1)^{|f|+1} d_W(f(d_V v)) + (-1)^{2|f|+1} f(d_V^2 v) \\
&= 0 - (-1)^{|f|} d_W(f(d_V v)) + (-1)^{|f|} d_W(f(d_V v)) + 0 = 0.
\end{align*}
The cancellation depends on the sign convention.
\end{verification}


\section{Cohomological versus homological grading}
\label{sec:cohom-vs-homol}


\begin{definition}[Grading conventions]
\label{def:grading-conventions}
Let $(C, d)$ be a differential graded object.
\begin{enumerate}[label=(\roman*)]
\item \emph{Homological grading.} $C = \bigoplus_{n \in \bZ} C_n$ with
$d: C_n \to C_{n-1}$. The differential \emph{lowers} degree by 1.
\item \emph{Cohomological grading.} $C = \bigoplus_{n \in \bZ} C^n$ with
$d: C^n \to C^{n+1}$. The differential \emph{raises} degree by 1.
\end{enumerate}
The translation is $C^n = C_{-n}$, which exchanges upper and lower indices.
\end{definition}

\begin{convention}[Standard conventions by context]
\label{conv:standard-by-context}
In this monograph:
\begin{enumerate}[label=(\roman*)]
\item \emph{Chain complexes of modules.} Homological convention $(C_\bullet, \partial)$.
\item \emph{Cochain complexes (de Rham, singular cochains).}
Cohomological convention $(C^\bullet, d)$.
\item \emph{Operadic bar/cobar.} Cohomological convention (translated from the homological convention of Loday--Vallette~\cite{LV12} via $C^n = C_{-n}$; see Definition~\ref{def:grading-conventions}).
\item \emph{Hochschild (co)homology.} Homological for homology $HH_*$,
cohomological for cohomology $HH^*$.
\item \emph{D-modules.} Cohomological convention, with de Rham complex
$\DR(\cM)$ in non-negative degrees.
\item \emph{$\infty$-categories.} Cohomological convention following
Lurie~\cite{HTT, HA}.
\end{enumerate}
\end{convention}

\begin{proposition}[Duality and grading reversal; \ClaimStatusProvedHere]
\label{prop:duality-grading}
For a finite-dimensional chain complex $(C_\bullet, \partial)$, the dual 
complex $C^* = \Hom(C, k)$ naturally carries a cohomological grading:
\[
(C^*)^n := \Hom_k(C_n, k) = (C_n)^*.
\]
The dual differential $\partial^*: (C^*)^n \to (C^*)^{n+1}$ is defined by:
\[
\langle \partial^* \phi, c \rangle := (-1)^{|\phi|+1} \langle \phi, \partial c \rangle
\]
for $\phi \in (C^*)^n$ and $c \in C_{n+1}$.
\end{proposition}

\begin{proof}
The sign ensures $(\partial^*)^2 = 0$:
\begin{align*}
\langle (\partial^*)^2 \phi, c \rangle 
&= (-1)^{|\phi|+2} \langle \partial^* \phi, \partial c \rangle 
= (-1)^{|\phi|+2} (-1)^{|\phi|+1} \langle \phi, \partial^2 c \rangle = 0.
\end{align*}
The sign $(-1)^{|\phi|+1}$ is precisely the convention that makes
$(C, C^*)$ into a duality pairing of chain complexes.
\end{proof}

\begin{definition}[Connective and coconnective]
\label{def:connective}
A chain complex $C$ (in homological grading) is:
\begin{enumerate}[label=(\roman*)]
\item \emph{Connective} if $C_n = 0$ for $n < 0$ (concentrated in non-negative degrees).
\item \emph{Coconnective} if $C_n = 0$ for $n > 0$ (concentrated in non-positive degrees).
\item \emph{Bounded} if both conditions hold with finitely many nonzero terms.
\end{enumerate}
In cohomological grading, connective means $C^n = 0$ for $n > 0$, and 
coconnective means $C^n = 0$ for $n < 0$.
\end{definition}

\begin{remark}[Filtrations and spectral sequences]
\label{rem:filt-ss-grading}
The grading convention affects the indexing of spectral sequences. For a 
filtered complex with cohomological grading and increasing filtration 
$F^p C \subseteq F^{p+1} C$, the spectral sequence has:
\[
E_r^{p,q} \Rightarrow H^{p+q}(C).
\]
For homological grading with decreasing filtration $F_p C \supseteq F_{p+1} C$:
\[
E^r_{p,q} \Rightarrow H_{p+q}(C).
\]
The bidegree conventions $(p, q)$ versus $(p, n-p)$ also vary by author.
\end{remark}


\section{Suspensions and desuspensions}
\label{sec:susp-desusp}


\begin{definition}[Suspension and desuspension]
\label{def:suspension}
\index{suspension!conventions}
\index{desuspension!conventions}
For a graded object $V = \bigoplus_n V^n$:
\begin{enumerate}[label=(\roman*)]
\item The \emph{suspension} $sV$ (also denoted $V[-1]$ in the cohomological convention or $V[1]$ in the homological convention; see Remark~\ref{rem:shift-notation}) is
defined by:
\[
(sV)^n := V^{n-1}.
\]
An element $v \in V^{n-1}$ corresponds to $sv \in (sV)^n$ with $|sv| = |v| + 1$.

\item The \emph{desuspension} $s^{-1}V$ (also denoted $V[1]$ in the cohomological convention or $V[-1]$ in the homological convention) is defined by:
\[
(s^{-1}V)^n := V^{n+1}.
\]
An element $v \in V^{n+1}$ corresponds to $s^{-1}v \in (s^{-1}V)^n$ with 
$|s^{-1}v| = |v| - 1$.
\end{enumerate}
These are inverse operations: $s \circ s^{-1} = s^{-1} \circ s = \id$.

The two constructions that produce the Koszul dual use \emph{opposite} shifts, for a precise reason:
\begin{itemize}
\item \emph{Bar construction} (desuspension): $\bar{B}(\cA) = T^c(s^{-1}\bar{\cA},\, d)$. Desuspension lowers generators by one degree because the bar differential $d_{\mathrm{res}}$ extracts a residue (an integration operation that lowers form degree), and the shift compensates so that $|d| = +1$.
\item \emph{Koszul dual coalgebra} (suspension): $\cA^! \hookrightarrow \mathrm{Cofree}(sV^*)$ (Appendix~\ref{app:koszul-reference}). Suspension raises the dual generators $V^*$ by one degree because dualizing reverses the grading, and the shift restores it.
\end{itemize}
These are consistent: when $\cA$ is Koszul, $H^*(\bar{B}(\cA))$ concentrates in bar degree~$1$, and the desuspension-then-suspension cancels, recovering the Koszul dual generators in their natural degree.
\end{definition}

\begin{remark}[Shift notation ambiguity]
\label{rem:shift-notation}
The notation $V[n]$ is used with two incompatible conventions in the literature:
\begin{enumerate}[label=(\roman*)]
\item \emph{Homological convention.} $(V[n])_k = V_{k-n}$, so $V[1]$ shifts
\emph{up} (increases indices).
\item \emph{Cohomological convention.} $(V[n])^k = V^{k+n}$, so $V[1]$ shifts 
\emph{down} (decreases indices in the sense that degree-$k$ elements come from 
degree-$(k+1)$ elements of $V$).
\end{enumerate}
We follow the cohomological convention: $V[n]^k = V^{k+n}$. Under this convention,
$sV = V[-1]$ (since $(V[-1])^k = V^{k-1} = (sV)^k$) and
$s^{-1}V = V[1]$ (since $(V[1])^k = V^{k+1} = (s^{-1}V)^k$).

\emph{Warning.} Many references in algebraic topology use the opposite convention where $sV = V[1]$; this corresponds to $(V[n])^k = V^{k-n}$ (the homological convention). When importing results from such references, all shift indices must be negated.
\end{remark}

\begin{proposition}[Suspension and differentials; \ClaimStatusProvedHere]
\label{prop:susp-diff}
If $(V, d)$ is a chain complex with $d: V^n \to V^{n+1}$, then $sV = V[-1]$
carries the \emph{suspended differential}:
\[
d_{sV}: (sV)^n \to (sV)^{n+1}, \quad d_{sV}(sv) := -s(dv).
\]
The sign ensures the suspension defines a functor on chain complexes (compatible with tensor products and the Koszul sign rule).
\end{proposition}

\begin{proof}
Without the sign, we would have $d_{sV}(sv) = s(dv)$, and then:
\[
d_{sV}^2(sv) = d_{sV}(s(dv)) = s(d(dv)) = s(d^2 v) = 0.
\]
This appears to work, but the sign is required for compatibility with tensor 
products. Consider $V \otimes W$ with differential:
\[
d_{V \otimes W}(v \otimes w) = dv \otimes w + (-1)^{|v|} v \otimes dw.
\]
For the suspended tensor product $(sV) \otimes W$ to have consistent differential:
\[
d((sv) \otimes w) = d_{sV}(sv) \otimes w + (-1)^{|sv|} sv \otimes dw 
= -s(dv) \otimes w + (-1)^{|v|+1} sv \otimes dw.
\]
This matches $s(d(v \otimes w))$ only with the sign convention $d_{sV}(sv) = -s(dv)$.
\end{proof}

\begin{corollary}[Iterated suspension \cite{LV12}; \ClaimStatusProvedElsewhere]
\label{cor:iterated-susp}
For $n$-fold suspension $s^n V = V[-n]$:
\[
d_{s^n V}(s^n v) = (-1)^n s^n(dv).
\]
The suspended element $s^n v$ has degree $|s^n v| = |v| + n$.
\end{corollary}

\begin{definition}[Suspension in operadic context]
\label{def:susp-operadic}
For an operad $\cP$, the \emph{operadic suspension} $\fS \cP$ is the operad with:
\[
(\fS \cP)(n) := \sgn_n \otimes \cP(n)[n-1]
\]
where $\sgn_n$ is the sign representation of $\Sigma_n$. The operadic composition 
involves signs from both the degree shift and the sign representation.

Explicitly, if $\gamma \in \cP(k)$ and $\mu_1, \ldots, \mu_k \in \cP(n_1), \ldots, \cP(n_k)$:
\[
s^{k-1}\gamma \circ (s^{n_1-1}\mu_1, \ldots, s^{n_k-1}\mu_k) 
= \epsilon \cdot s^{n-1}(\gamma \circ (\mu_1, \ldots, \mu_k))
\]
where $n = n_1 + \cdots + n_k$ and $\epsilon$ is a sign depending on degrees 
and positions.
\end{definition}

\begin{proposition}[Suspension and Koszul duality \cite{LV12}; \ClaimStatusProvedElsewhere]
\label{prop:susp-koszul}
For a Koszul operad $\cP$, the Koszul dual cooperad is:
\[
\cP^{\scriptstyle \text{\textexclamdown}} = (\fS^{-1} \cP^!)^\vee
\]
where $\cP^!$ is the linear dual operad and $\fS^{-1}$ is operadic desuspension. 
Explicitly:
\[
\cP^{\scriptstyle \text{\textexclamdown}}(n) = \cP^!(n)^* \otimes \sgn_n[1-n].
\]
This formula explains the appearance of signs and shifts in bar-cobar duality.
\end{proposition}


\section{Determinant lines}
\label{sec:det-lines}

\begin{definition}[Determinant of a vector space]
\label{def:det-vect}
For a finite-dimensional vector space $V$ of dimension $n$, the 
\emph{determinant line} is:
\[
\Det(V) := \bigwedge^n V = \bigwedge^{\dim V} V.
\]
This is a 1-dimensional vector space. An element $\omega \in \Det(V) \setminus \{0\}$ 
is called an \emph{orientation} of $V$.
\end{definition}

\begin{proposition}[Properties of determinant lines \cite{Weibel94}; \ClaimStatusProvedElsewhere]
\label{prop:det-properties}
The determinant construction satisfies:
\begin{enumerate}[label=(\roman*)]
\item \emph{Short exact sequences.} For $0 \to U \to V \to W \to 0$ exact,
\[
\Det(V) \cong \Det(U) \otimes \Det(W).
\]
\item \emph{Direct sums.} $\Det(V \oplus W) \cong \Det(V) \otimes \Det(W)$.
\item \emph{Duality.} $\Det(V^*) \cong \Det(V)^* = \Det(V)^{-1}$.
\item \emph{Zero space.} $\Det(0) = k$ (the ground field, concentrated in degree 0).
\item \emph{Functoriality.} An isomorphism $f: V \xrightarrow{\sim} W$ induces 
$\Det(f): \Det(V) \xrightarrow{\sim} \Det(W)$ with $\Det(f)(v_1 \wedge \cdots \wedge v_n) 
= f(v_1) \wedge \cdots \wedge f(v_n)$.
\end{enumerate}
\end{proposition}

\begin{definition}[Determinant of a finite set]
\label{def:det-set}
For a finite set $I$, define:
\[
\Det(I) := \Det(k^I)
\]
where $k^I$ is the vector space with basis indexed by $I$. Concretely, if 
$I = \{i_1, \ldots, i_n\}$:
\[
\Det(I) = k \cdot (e_{i_1} \wedge \cdots \wedge e_{i_n})
\]
is 1-dimensional, and permuting the order of $I$ introduces signs according to 
the permutation's signature.
\end{definition}

\begin{lemma}[Determinant and ordering \cite{Weibel94}; \ClaimStatusProvedElsewhere]
\label{lem:det-ordering}
For a finite set $I$ with total orderings $<$ and $<'$, let $\sigma \in \Sigma_I$ 
be the permutation taking the $<$-ordering to the $<'$-ordering. Then:
\[
e_{i_1} \wedge \cdots \wedge e_{i_n} = \sgn(\sigma) \cdot e_{i_{\sigma(1)}} \wedge \cdots \wedge e_{i_{\sigma(n)}}.
\]
The determinant line $\Det(I)$ is canonically independent of ordering, but a 
choice of generator (i.e., orientation) depends on ordering.
\end{lemma}

\begin{definition}[Orientation line]
\label{def:orientation-line}
For a smooth manifold $M$ of dimension $d$, the \emph{orientation line} at 
$p \in M$ is:
\[
\orline{M,p} := \Det(T_p M) = \bigwedge^d T_p M.
\]
The \emph{orientation sheaf} $\orline{M}$ is the local system with fiber 
$\orline{M,p}$ at $p$. An orientation of $M$ is a global section 
$\sigma: M \to \orline{M}$ that is nowhere vanishing.
\end{definition}

\begin{proposition}[Determinant lines on configuration spaces \cite{FM94}; \ClaimStatusProvedElsewhere]
\label{prop:det-config}
For the configuration space $\Conf_n(X)$ of a curve $X$:
\begin{enumerate}[label=(\roman*)]
\item The tangent space at $(z_1, \ldots, z_n) \in \Conf_n(X)$ is:
\[
T_{(z_1, \ldots, z_n)} \Conf_n(X) = \bigoplus_{i=1}^n T_{z_i} X.
\]
\item The determinant line is:
\[
\Det(T\Conf_n(X)) = \bigotimes_{i=1}^n \Det(T_{z_i} X) = \bigotimes_{i=1}^n \omega_{X,z_i}^{-1}
\]
where $\omega_X = \Det(T^*X)$ is the canonical bundle.
\item For the Fulton--MacPherson compactification $\FM_n(X)$:
\[
\Det(T\FM_n(X)) \cong \Det(T\Conf_n(X)) \otimes \Det(N_{D/\FM_n})
\]
where $N_{D/\FM_n}$ is the normal bundle to the boundary divisor.
\end{enumerate}
\end{proposition}

\begin{construction}[Determinant line in bar complex]
\label{constr:det-bar}
In the geometric bar complex, the determinant line appears through the 
identification:
\[
\Bbar^{\mathrm{geom}}_n(\cA) = \Gamma(\FM_n(X), \cA^{\boxtimes n} \otimes \Omega^{n-1}_{\log}(\FM_n, D))
\]
The logarithmic $(n-1)$-forms can be written as:
\[
\Omega^{n-1}_{\log}(\FM_n, D) \cong \omega_{\FM_n} \otimes \Det(N_D)^{-1}[1-n]
\]
tracking the relationship between the canonical bundle and boundary geometry.

Explicitly, for $n = 2$ on $X = \bP^1$:
\[
\Omega^1_{\log}(\FM_2(\bP^1), D_{12}) = \cO \cdot \dlog(z_1 - z_2) = \cO \cdot \frac{d(z_1 - z_2)}{z_1 - z_2}
\]
which has a simple pole along $D_{12} = \{z_1 = z_2\}$ and generates the 
log de Rham complex.
\end{construction}

\begin{proposition}[Determinant and residues \cite{Har77}; \ClaimStatusProvedElsewhere]
\label{prop:det-residue}
The residue map along a divisor $D \subset Y$ is:
\[
\Res_D: \Omega^k_{\log}(Y, D) \to \Omega^{k-1}(D)
\]
This map respects determinant lines in the following sense: if $D$ is smooth 
of codimension 1, then:
\[
\Res_D: \omega_Y \otimes \cO_Y(D)|_D \to \omega_D
\]
is the adjunction isomorphism, and the signs in the bar differential arise 
from tracking this isomorphism across multiple boundary strata.
\end{proposition}

\begin{theorem}[Determinant conventions and bar-cobar signs \cite{LV12}; \ClaimStatusProvedElsewhere]
\label{thm:det-bar-cobar-signs}
The signs in the bar-cobar adjunction can be uniformly expressed using 
determinant lines. For an $\Eone$-chiral algebra $\cA$:
\begin{enumerate}[label=(\roman*)]
\item The bar complex element $[a_1 | \cdots | a_n] \in \Bbar_n(\cA)$ corresponds to:
\[
a_1 \otimes \cdots \otimes a_n \otimes \omega_{[n]} \in \cA^{\otimes n} \otimes \Det([n])
\]
where $[n] = \{1, \ldots, n\}$ and $\omega_{[n]}$ is the standard generator of 
$\Det([n])$ determined by the ordering $1 < 2 < \cdots < n$.

\item The bar differential is:
\[
d[a_1 | \cdots | a_n] = \sum_{i=1}^{n-1} (-1)^{\epsilon_i} [a_1 | \cdots | a_i a_{i+1} | \cdots | a_n]
\]
where $\epsilon_i = |a_1| + \cdots + |a_i| + i - 1$ tracks both internal degrees 
and position.

\item These signs arise canonically from the face maps of the simplicial 
structure on $\Delta^\bullet$ and the determinant line conventions.
\end{enumerate}
\end{theorem}


\section{Detailed sign computations in bar-cobar duality}
\label{sec:detailed-signs}

\begin{computation}[Bar differential signs: degree 2 to 1]
\label{comp:bar-signs-2-1}
For elements $[a|b] \in \Bbar_2(A)$ where $A$ is a dg-algebra:
\[
d_{\mathrm{bar}}[a|b] = [ab] - (-1)^{|a|} a \cdot [b] - [a] \cdot b
\]
Here:
\begin{enumerate}[label=(\roman*)]
\item The term $[ab]$ comes from the multiplication $\mu: A \otimes A \to A$.
\item The term $(-1)^{|a|} a \cdot [b]$ is the left action of $A$ on $\Bbar_1(A) = A$.
\item The term $[a] \cdot b$ is the right action.
\end{enumerate}

For the \emph{reduced} bar complex $\overline{\Bbar}(A) = \Bbar(A, A, k)$:
\[
d_{\mathrm{bar}}[a|b] = [ab]
\]
with augmentation eliminating the action terms.
\end{computation}

\begin{computation}[Bar differential signs: degree 3 to 2]
\label{comp:bar-signs-3-2}
For $[a|b|c] \in \Bbar_3(A)$:
\begin{align*}
d_{\mathrm{bar}}[a|b|c] &= [ab|c] - (-1)^{|a|}[a|bc] \\
&\quad + (-1)^{|a|} a \cdot [b|c] + (-1)^{|a|+|b|} [a|b] \cdot c \\
&\quad + (-1)^{|a|} [da|b|c] + (-1)^{|a|+|b|+1} [a|db|c] + (-1)^{|a|+|b|+|c|} [a|b|dc]
\end{align*}

The signs arise systematically:
\begin{enumerate}[label=(\roman*)]
\item $[ab|c]$: Multiply positions 1,2; no sign (conventions place multiplication first).
\item $(-1)^{|a|}[a|bc]$: Multiply positions 2,3; sign from passing $a$ over boundary.
\item Action terms: Signs from Koszul rule and boundary conventions.
\item Differential terms: Signs from position in the bar expression.
\end{enumerate}
\end{computation}

\begin{computation}[Cobar differential signs: degree 1 to 2]
\label{comp:cobar-signs-1-2}
For a coassociative coalgebra $C$ with coproduct $\Delta$, the cobar construction
$\Omega(C) = T(s^{-1}\overline{C})$ has differential on generators:
\[
d_\Omega(s^{-1}c) = -s^{-1}(dc) - \sum_{(c)} (-1)^{|c'|} (s^{-1}c') \otimes (s^{-1}c'')
\]
where $\Delta(c) = \sum_{(c)} c' \otimes c''$ (Sweedler notation) and the desuspended element $s^{-1}c'$ has degree $|s^{-1}c'| = |c'| - 1$.

\emph{Sign verification.} The Koszul sign $(-1)^{|c'|}$ within each summand
arises from applying $(s^{-1} \otimes s^{-1})$ to $c' \otimes c''$: commuting
the second $s^{-1}$ (degree $-1$) past $c'$ gives $(-1)^{|s^{-1}|\cdot|c'|}
= (-1)^{|c'|}$. The overall minus sign on the comultiplication term is
required for compatibility with the bar differential convention
$d_{\mathrm{bar}}[a|b] = (-1)^{|a|}[ab]$ (desuspension, Computation~\ref{comp:bar-signs-2-1}):
the bar-cobar counit $\varepsilon\colon \Omega(\bar B(A)) \to A$ is a chain map
only when both terms of $d_\Omega$ carry the same overall sign.
% NOTE (2026-03-31): The $-\sum$ sign on the comultiplication term differs from
% [LV12, Prop.~2.2.5], which uses $+\sum$ under the SUSPENSION convention.
% Our DESUSPENSION convention flips this sign; see eq:cobar-diff-generators.
\end{computation}

\begin{computation}[Cobar differential signs: degree 2 to 3]
\label{comp:cobar-signs-2-3}
For a tensor $s^{-1}c_1 \otimes s^{-1}c_2 \in \Omega_2(C)$:
\begin{align*}
d_\Omega(s^{-1}c_1 \otimes s^{-1}c_2) &= d_\Omega(s^{-1}c_1) \otimes s^{-1}c_2
 + (-1)^{|s^{-1}c_1|} s^{-1}c_1 \otimes d_\Omega(s^{-1}c_2) \\
&= \Bigl( -s^{-1}(dc_1) - \sum (-1)^{|c_1'|} s^{-1}c_1' \otimes s^{-1}c_1'' \Bigr) \otimes s^{-1}c_2 \\
&\quad + (-1)^{|c_1|-1} s^{-1}c_1 \otimes \Bigl( -s^{-1}(dc_2) - \sum (-1)^{|c_2'|} s^{-1}c_2' \otimes s^{-1}c_2'' \Bigr)
\end{align*}

Expanding:
\begin{align*}
d_\Omega(s^{-1}c_1 \otimes s^{-1}c_2) &= -s^{-1}(dc_1) \otimes s^{-1}c_2 \\
&\quad - \sum (-1)^{|c_1'|} s^{-1}c_1' \otimes s^{-1}c_1'' \otimes s^{-1}c_2 \\
&\quad + (-1)^{|c_1|} s^{-1}c_1 \otimes s^{-1}(dc_2) \\
&\quad + (-1)^{|c_1|} \sum (-1)^{|c_2'|} s^{-1}c_1 \otimes s^{-1}c_2' \otimes s^{-1}c_2''
\end{align*}
\end{computation}

\begin{proposition}[Master sign formula {\cite{LV12}}; \ClaimStatusProvedElsewhere]
\label{prop:master-sign}
For the bar complex of an $\Ainf$-algebra $(A, \{m_n\})$, the full differential 
on $[a_1|\cdots|a_n]$ is:
\[
d_{\mathrm{bar}}[a_1|\cdots|a_n] = \sum_{i=1}^{n} \sum_{k=1}^{n-i+1} 
(-1)^{\epsilon_{i,k}} [a_1|\cdots|a_{i-1}|m_k(a_i, \ldots, a_{i+k-1})|a_{i+k}|\cdots|a_n]
\]
where the sign is:
\[
\epsilon_{i,k} = \sum_{j=1}^{i-1} (|a_j| - 1) + \sum_{j=i}^{i+k-2} |a_j|
\]
where the first sum is the \emph{coderivation sign} (from commuting past
$s^{-1}a_1, \ldots, s^{-1}a_{i-1}$) and the second is the \emph{desuspension sign}
from $b_k(s^{-1}a_i, \ldots, s^{-1}a_{i+k-1})$.

\begin{remark}[Sign convention comparison]
Some references (e.g., Loday--Vallette \cite{LV12}) define the bar differential
on $sa_1 \otimes \cdots \otimes sa_n$ with a sign
$\epsilon'_{i,k} = \sum_{j=1}^{i-1}|sa_j|$ arising from commuting the coderivation past
suspended elements. For a strict algebra ($m_k = 0$ for $k \neq 2$), the two conventions
are related by a global sign on each summand and yield the same $d^2 = 0$ complex.
The explicit computations in \S\ref{comp:bar-signs-2-1}--\ref{comp:bar-signs-3-2}
use the \emph{unsuspended} bar notation ($[a|b] = a \otimes b$). In the desuspended convention ($[a|b] = s^{-1}a \otimes s^{-1}b$), the correct formulas are
$d[a|b] = (-1)^{|a|}[ab]$ and $d[a|b|c] = (-1)^{|a|}[ab|c] - (-1)^{|a|+|b|}[a|bc]$; see the verification in \S\ref{ver:d2-degree3}.
\end{remark}
\end{proposition}

\medskip
\noindent\textbf{Convention shift.} The computations above (\S\ref{comp:bar-signs-2-1}--\ref{comp:bar-signs-3-2}) use the unsuspended bar notation $[a|b] = a \otimes b$. From this point onward, we work in the \emph{desuspended} convention $[a|b] = s^{-1}a \otimes s^{-1}b$, which is the convention used in the body of the monograph.

\begin{verification}[\texorpdfstring{$d^2 = 0$}{d\textasciicircum 2 = 0} check at degree 3]
\label{ver:d2-degree3}
We verify $d_{\mathrm{bar}}^2[a|b|c] = 0$ for a graded associative algebra
(where $m_2 = \mu$ and $m_k = 0$ for $k \neq 2$).

The desuspended multiplication on $s^{-1}A$ carries a Koszul sign:
$b_2(s^{-1}a, s^{-1}b) = (-1)^{|a|} s^{-1}(ab)$. The coderivation extension
to $T^c(s^{-1}\bar{A})$ gives:
\begin{align*}
d_{\mathrm{bar}}[a|b] &= (-1)^{|a|}[ab], \\
d_{\mathrm{bar}}[a|b|c] &= (-1)^{|a|}[ab|c] - (-1)^{|a|+|b|}[a|bc].
\end{align*}
(The sign at position $i$ is $(-1)^{\sum_{j<i}(|a_j|-1) + |a_i|}$.)

Applying $d_{\mathrm{bar}}$ again:
\begin{align*}
d_{\mathrm{bar}}^2[a|b|c] &= (-1)^{|a|} d_{\mathrm{bar}}[ab|c]
 - (-1)^{|a|+|b|} d_{\mathrm{bar}}[a|bc] \\
&= (-1)^{|a|} \cdot (-1)^{|a|+|b|} [(ab)c]
 - (-1)^{|a|+|b|} \cdot (-1)^{|a|} [a(bc)] \\
&= (-1)^{|b|}\bigl[(ab)c - a(bc)\bigr] = 0
\end{align*}
by associativity.

\begin{remark}
For generators concentrated in degree~0 (the ungraded case), all signs are
trivial and the formulas simplify to $d[a|b] = [ab]$ and
$d[a|b|c] = [ab|c] - [a|bc]$, recovering the expressions in
Computations~\ref{comp:bar-signs-2-1}--\ref{comp:bar-signs-3-2}.
\end{remark}
\end{verification}


\section{Determinant lines and stratifications}
\label{sec:det-strat}

\begin{definition}[Orientation system]
\label{def:orientation-system}
An \emph{orientation system} on a stratified space $Y = \bigsqcup_\alpha Y_\alpha$ 
is a collection of line bundles $\orline{Y_\alpha}$ on each stratum together with 
\emph{gluing isomorphisms}: for each pair $Y_\alpha \subseteq \overline{Y_\beta}$ 
(closure relation), an isomorphism:
\[
\phi_{\alpha\beta}: \orline{Y_\alpha}|_{\partial_\alpha Y_\beta} \xrightarrow{\sim} 
\orline{Y_\beta}|_{\partial_\alpha Y_\beta} \otimes N_{\alpha\beta}
\]
where $N_{\alpha\beta}$ is the normal bundle factor and $\partial_\alpha Y_\beta$ 
is the boundary of $Y_\beta$ meeting $Y_\alpha$.
\end{definition}

\begin{proposition}[Orientation system on FM compactification \cite{FM94}; \ClaimStatusProvedElsewhere]
\label{prop:orient-fm}
The FM compactification $\FM_n(X)$ carries a canonical orientation system 
determined by:
\begin{enumerate}[label=(\roman*)]
\item On the open stratum $\Conf_n(X)$: $\orline{\Conf_n(X)} = \bigotimes_{i=1}^n \orline{X}$.
\item On boundary stratum $D_T$ (labeled by tree $T$): 
$\orline{D_T} = \bigotimes_{v \in V(T)} \orline{X}$ times exceptional fiber orientations.
\item Gluing isomorphisms: Given by the blowup construction, with signs determined 
by the ordering on vertices of $T$.
\end{enumerate}
\end{proposition}

\begin{construction}[Sign from blowup]
\label{constr:sign-blowup}
When blowing up the diagonal $\Delta_{ij} \subset X^n$, the orientation 
transformation is:
\[
\orline{X^n} = \orline{\Bl_{\Delta_{ij}}(X^n)} \otimes \orline{E_{ij}}^{-1}
\]
where $E_{ij} \cong \bP(N_{\Delta_{ij}/X^n})$ is the exceptional divisor.

For $X$ a curve (dimension 1), the normal bundle $N_{\Delta/X^2} \cong T_X$ 
along the diagonal, so:
\[
\orline{E_{ij}} = \orline{\bP^0} = k
\]
is canonically trivial, and no orientation sign arises from the blowup in this case.
\end{construction}

\begin{lemma}[Residue and orientation \cite{FM94, Har77}; \ClaimStatusProvedElsewhere]
\label{lem:residue-orient}
The residue map $\Res_{D_{ij}}: \Omega^k_{\log}(\FM_n, D) \to \Omega^{k-1}(D_{ij})$
is compatible with orientations:
\[
\Res_{D_{ij}}(\omega \wedge \dlog(z_i - z_j)) = \omega|_{D_{ij}}
\]
with sign conventions:
\begin{enumerate}[label=(\roman*)]
\item If $\omega = f(z_1, \ldots, z_n) \, dz_1 \wedge \cdots \wedge \widehat{dz_i} \wedge \cdots \wedge dz_n$
(omitting $dz_i$), then:
\[
\Res_{D_{ij}}(\omega \wedge \dlog(z_i - z_j)) = (-1)^{i-1} f|_{z_i = z_j} \,
dz_1 \wedge \cdots \wedge \widehat{dz_i} \wedge \cdots \wedge dz_n|_{D_{ij}}.
\]
\item The sign $(-1)^{i-1}$ accounts for moving $\dlog(z_i - z_j)$ to the position
where $dz_i$ would appear.
\end{enumerate}
\end{lemma}


%% ======================================================================
%% Dictionary of sign conventions
%% (Merged from former appendices/sign_conventions.tex)
%% ======================================================================

\section{Dictionary of sign conventions}
\label{app:sign-conventions}

Sign conventions used in different sources are compared and translated below.

\subsection{Loday--Vallette vs. this manuscript}

\begin{center}
\begin{longtable}{|>{\raggedright\arraybackslash}p{5.8cm}|>{\raggedright\arraybackslash}p{3.9cm}|>{\raggedright\arraybackslash}p{3.9cm}|}
\caption{Sign convention comparison} \\
\hline
\textbf{Object/Operation} & \textbf{Loday--Vallette \cite{LV12}} & \textbf{This Manuscript} \\
\hline
\endfirsthead
\multicolumn{3}{c}{\tablename\ \thetable\ -- \textit{Continued}} \\
\hline
\textbf{Object/Operation} & \textbf{Loday--Vallette} & \textbf{This Manuscript} \\
\hline
\endhead
\hline
\endfoot
\hline
\endlastfoot
Koszul sign rule & $(-1)^{|a| \cdot |b|}$ & $(-1)^{|a| \cdot |b|}$ (same) \\
Differential degree & $|d| = -1$ & $|d| = +1$ \\
Suspension & $s: V \to sV$, $|sv| = |v| + 1$ & $s: V \to V[-1]$, $|sv| = |v| + 1$ (cohomological: $V[-1]^k = V^{k-1}$, so $v \in V^m$ maps to $sV^{m+1}$) \\
Desuspension & $s^{-1}: sV \to V$, $|s^{-1}(sv)| = |v|$ & $[-1]: V[1] \to V$ \\
Bar construction & $B(\mathcal{A}) = (T^c(s\mathcal{A}), d_{\text{bar}})$ & $\bar{B}(\mathcal{A}) = (T^c(s^{-1}\bar{\mathcal{A}}), d)$ (desuspension; cf.\ cohomological convention) \\
Cobar construction & $\Omega(\mathcal{C}) = (T(s^{-1}\mathcal{C}), d_{\text{cobar}})$ & $\Omega(\mathcal{C})_n = \mathcal{C}^{\otimes_{\text{co}} n}$ \\
Coproduct sign & $\Delta(ab) = \Delta(a) \cdot \Delta(b)$ with $(-1)^{|a_2| \cdot |b_1|}$ & Same \\
Shuffle sign & $(a \shuffle b) = \sum (-1)^{\sigma} a_{\sigma(1)} \otimes \cdots$ & Same \\
Collision divisor ordering & Not applicable (no geometry) & Lexicographic: $i < j$ always \\
Logarithmic form sign & Not applicable & $\eta_{ji} = \eta_{ij}$ as differential forms ($d\log(-1)=0$). Note: the Orlik--Solomon generators are antisymmetric; fixing $i < j$ in $\eta_{ij}$ fixes an orientation. \\
Arnold relations & Not applicable & $\sum_{\text{cyclic}} \eta_{ij} \wedge \eta_{jk} = 0$ \\
\end{longtable}
\end{center}

\subsubsection{Key differences explained}

\emph{1.~Differential degree.}
Loday--Vallette use homological grading ($|d| = -1$); this manuscript uses cohomological grading ($|d| = +1$).

\emph{Translation.} If $(C_*, d)$ is a chain complex in LV convention ($d: C_n \to C_{n-1}$), set $C^n := C_{-n}$ with the same underlying map~$d$, which now raises cohomological degree by~$1$. No sign change is needed: $d_{\text{us}} = d_{\text{LV}}$ (as linear maps).

\emph{2.~Suspension.}
Loday--Vallette treat suspension $s$ as an explicit operator; this manuscript uses the degree shift $sV = V[-1]$, so $|sv| = |v| + 1$.

\emph{Translation.} $sV$ (LV) corresponds to $V[-1]$ (us), i.e., our $sV$. Both raise degree by~$1$: LV's convention $(sV)_k = V_{k-1}$ translates via $\deg_{\mathrm{coh}} = -\deg_{\mathrm{hom}}$ to $(sV)^k = V^{k-1} = (V[-1])^k$.

\emph{3.~Bar/cobar formulas.}
Loday--Vallette include explicit suspension in the formula; this manuscript absorbs it into the D-module structure.

\emph{Translation.} Our $\bar{B}_n(\mathcal{A})$ corresponds to LV's $B(\mathcal{A})$ in degree $n$ after removing the suspension $s$.

\subsection{Beilinson--Drinfeld vs. this manuscript}

\begin{center}
\begin{tabular}{|>{\raggedright\arraybackslash}p{5.8cm}|>{\raggedright\arraybackslash}p{3.9cm}|>{\raggedright\arraybackslash}p{3.9cm}|}
\hline
\textbf{Object/Operation} & \textbf{BD \cite{BD04}} & \textbf{This Manuscript} \\
\hline
Chiral algebra & $\mathcal{A}$ (D-module) & $\mathcal{A}$ (same) \\
Factorization & $j_{!*}\mathcal{A}$ & Implicit in $\ConfigSpace{n}$ \\
Configuration space & $\text{Ran}(X)$ & $\bigcup_n \ConfigSpace{n}$ \\
Collision divisor & $(i,j)^c$ (complement) & $\omitpair{i}{j}$ (hat notation) \\
Chiral connection & $\nabla$ & $\nabla$ (same) \\
Residue & Implicit in factorization & Explicit via $\text{Res}_{z_i \to z_j}$ \\
OPE & Encoded in $\mathcal{A}(D)$ & Explicit: $a(z)b(w) = \sum c_n(w)/(z-w)^n$ \\
Koszul duality & Not discussed (BD focus on one side) & Central theme \\
\hline
\end{tabular}
\end{center}

\subsubsection{Key differences explained}

\emph{BD's approach.}
\begin{itemize}
\item Ran space formulation (taking colimits over all $n$)
\item Factorization axiom as the primary structure
\item D-modules as the fundamental objects
\item No explicit bar/cobar constructions
\end{itemize}

\emph{This monograph.}
\begin{itemize}
\item Explicit configuration spaces $\ConfigSpace{n}$ for each $n$
\item Bar complex as an explicit resolution
\item Koszul duality as the organizing principle
\item Geometric realization via residues
\end{itemize}

\emph{Translation.} Our bar complex $\bar{B}_*(\mathcal{A})$ is the ``Chevalley--Cousin resolution'' of $\mathcal{A}$ viewed as a factorization algebra in BD's sense (BD Theorem 3.4.9).

\subsection{Costello--Gwilliam vs. this manuscript}

\begin{center}
\begin{tabular}{|>{\raggedright\arraybackslash}p{5.8cm}|>{\raggedright\arraybackslash}p{3.9cm}|>{\raggedright\arraybackslash}p{3.9cm}|}
\hline
\textbf{Object/Operation} & \textbf{CG \cite{CG17}} & \textbf{This Manuscript} \\
\hline
Factorization algebra & $\mathcal{F}$ (precosheaf) & $\mathcal{A}$ (chiral algebra) \\
Configuration space & $\text{Conf}_n(M)$ & $\ConfigSpace{n}$ \\
Compactification & Fulton--MacPherson & Same \\
Bar complex & Not emphasized & Central construction \\
Feynman diagrams & Graph complex & Genus-stratified bar complex \\
Renormalization & BV formalism & Completion of bar complex \\
Quantum corrections & Loop order & Genus $g$ \\
\hline
\end{tabular}
\end{center}

\subsubsection{Key differences explained}

\emph{CG's approach.}
\begin{itemize}
\item Factorization algebras on manifolds (any dimension)
\item Feynman diagram expansion for observables
\item BV formalism for quantization
\item Emphasis on renormalization and effective field theory
\end{itemize}

\emph{This monograph.}
\begin{itemize}
\item Chiral algebras on curves (1-dimensional)
\item Genus expansion instead of loop expansion
\item Bar-cobar construction and Koszul duality instead of BV
\item Emphasis on algebraic structure and representation theory
\end{itemize}

\emph{Translation.}
\begin{itemize}
\item CG's ``factorization algebra'' on a curve $X$ = BD/Our ``chiral algebra''
\item CG's ``observable'' = Our ``element of $\mathcal{A}$''
\item CG's ``1-loop graph'' = Our ``genus-1 contribution to bar complex''
\item CG's ``renormalization'' = Our ``nilpotent completion of bar complex''
\end{itemize}

\subsection{Kontsevich vs. this manuscript}

\begin{center}
\begin{tabular}{|>{\raggedright\arraybackslash}p{5.8cm}|>{\raggedright\arraybackslash}p{3.9cm}|>{\raggedright\arraybackslash}p{3.9cm}|}
\hline
\textbf{Object/Operation} & \textbf{Kontsevich \cite{Kon99}} & \textbf{This Manuscript} \\
\hline
Configuration space & $C_n(\mathbb{R}^d)$ (open) & $\ConfigSpace{n}$ (compactified) \\
Forms & Smooth forms & Logarithmic forms \\
Propagator & $\frac{1}{z-w}$ & $\frac{dz}{z-w}$ (with log pole) \\
Graphs & Directed graphs & Genus-stratified graphs \\
Formality & $\mathcal{U}: T_{\text{poly}} \to D_{\text{poly}}$ & Bar-cobar: $\bar{B} \dashv \Omega$ \\
Wheels & Non-planar graphs & Higher genus contributions \\
\hline
\end{tabular}
\end{center}

\subsubsection{Key differences explained}

\emph{Kontsevich's formality.}
\begin{itemize}
\item Classical: Poisson manifolds $\to$ deformation quantization
\item Configuration spaces in $\mathbb{R}^d$ (no compactification)
\item Smooth forms (no poles)
\item Graph complex (combinatorial)
\end{itemize}

\emph{Our chiral formality.}
\begin{itemize}
\item Coisson algebras (PVA) $\to$ vertex algebras (OPE) via chiral configuration spaces
\item Configuration spaces on curves (compactified)
\item Logarithmic forms (poles at collisions)
\item Genus-stratified complex (geometric)
\end{itemize}

\emph{Relation.} Kontsevich's formality is the \emph{genus-0 part} of chiral formality. The bar-cobar framework extends Kontsevich to include all genera (higher-loop corrections).

\subsection{Summary table: all conventions}

See Table~\ref{tab:master-comparison-signs} in \S\ref{sec:master-comparison-signs} for the complete comparison across all four sources. The one essential difference: Loday--Vallette use $|d|=-1$; all other sources (BD, CG, this manuscript) use $|d|=+1$.

\subsection{Practical guide: how to translate}

\subsubsection{From Loday--Vallette to our conventions}

\emph{Rule~1.} Replace $|d| = -1$ with $|d| = +1$.

\emph{Rule~2.} Replace LV's suspension $s$ with our degree shift $[-1]$: $sV = V[-1]$.

\emph{Rule~3.} Our geometric forms $\Omega^n(\log D)$ correspond to LV's suspended generators $s^n V$.

\subsubsection{From Beilinson--Drinfeld to our conventions}

\emph{Rule~1.} BD's $j_{!*}$ (factorization pushforward) = our explicit configuration space integral.

\emph{Rule~2.} BD's Ran space $\text{Ran}(X)$ = our $\bigcup_n \ConfigSpace{n} / \sim$ (colimit).

\emph{Rule~3.} BD's ``chiral product'' = our ``OPE residue''

\subsubsection{From Costello--Gwilliam to our conventions}

\emph{Rule~1.} CG's ``1-loop'' = our ``genus 1''

\emph{Rule~2.} CG's ``renormalization'' = our ``$I$-adic completion''

\emph{Rule~3.} CG's BV bracket = our bar differential (when specialized to curves).

\subsection{Examples of translation}

\begin{example}[Translating a bar differential formula from LV]
\emph{Loday--Vallette writes.}
\[d_{LV}(s a_1 \otimes s a_2 \otimes s a_3) = (-1)^{|a_1|} (s[a_1, a_2] \otimes s a_3) + \cdots\]

\emph{Our notation.}
\[d(a_1 \otimes a_2 \otimes a_3 \otimes \omega_2) = ([a_1, a_2] \otimes a_3 \otimes \text{Res}[\omega_2]) + \cdots\]

\emph{Translation.}
\begin{itemize}
\item Remove explicit suspension $s$ (implicit in form degree)
\item Change sign convention: $(-1)^{|a_1|}$ becomes automatic from Koszul rule
\item Add geometric form $\omega_2 \in \Omega^2(\log D)$
\end{itemize}
\end{example}

\begin{example}[Translating a BD factorization formula]
\emph{Beilinson--Drinfeld writes.}
\[j_{!*}(\mathcal{A} \boxtimes \mathcal{A})|_{U \sqcup V} \simeq j_{!*}\mathcal{A}|_U \boxtimes j_{!*}\mathcal{A}|_V\]

\emph{Our notation.}
\[\barcomplex{1}{\mathcal{A}}|_{U \sqcup V} = \int_{C_2(U) \sqcup C_2(V)} \mathcal{A}^{\boxtimes 2} \otimes \Omega^1_{\log} \simeq \barcomplex{1}{\mathcal{A}}|_U \otimes \barcomplex{1}{\mathcal{A}}|_V\]

\emph{Translation.}
\begin{itemize}
\item $j_{!*}$ (pushforward) = configuration space integral
\item Factorization isomorphism = bar complex splitting
\item Add explicit forms $\Omega^1_{\log}$
\end{itemize}
\end{example}

\subsection{Sign rules for this manuscript}

For easy reference, here are ALL sign rules used in this manuscript in one place:

\subsubsection{Koszul signs}

\emph{Rule.} When permuting two graded objects $a$ and $b$:
\[a \otimes b = (-1)^{|a| \cdot |b|} b \otimes a\]

\emph{Application.} Moving a form $\omega$ of degree $|\omega| = n$ past fields $\phi_1, \ldots, \phi_k$:
\[(\phi_1 \otimes \cdots \otimes \phi_k) \otimes \omega = (-1)^{n(|\phi_1| + \cdots + |\phi_k|)} \omega \otimes (\phi_1 \otimes \cdots \otimes \phi_k)\]

\subsubsection{Collision divisor signs}

\emph{Rule.} Collision divisors are always written with indices in increasing order: $\colldiv{i}{j}$ means $i < j$.

\emph{Convention.} We write $\colldiv{i}{j}$ with $i < j$. Geometrically $D_{ij} = D_{ji}$ (same subvariety $z_i = z_j$). The sign convention $\colldiv{j}{i} = -\colldiv{i}{j}$ applies to the \emph{oriented divisor} (i.e., to the associated residue forms, not the subvariety itself).

\subsubsection{Arnold relation signs}

\emph{3-term Arnold relation.}
\[\LogForm{i}{j} \wedge \LogForm{j}{k} + \LogForm{j}{k} \wedge \LogForm{k}{i} + \LogForm{k}{i} \wedge \LogForm{i}{j} = 0\]

\emph{Higher-degree consequences.}
All higher-degree relations in the OS algebra follow from the 3-term Arnold relations by repeated application. There is no independent ``general Arnold relation'' beyond the 3-term version.

\subsubsection{Residue signs}

The sign arising from the residue at $\colldiv{i}{j}$ is determined by the Koszul sign rule: the residue operation (cohomological degree~$1$) must commute past the preceding tensor factors. For elements $s^{-1}a_1 \otimes \cdots \otimes s^{-1}a_n$ in the bar complex, the residue at $D_{ij}$ (colliding factors $i$ and $j$) picks up the sign $(-1)^{\sum_{k<i}|s^{-1}a_k|}$. In particular, when all generators have even desuspended degree, all residue signs are positive.

For the explicit sign computations relevant to the bar differential, see the proof of $d^2 = 0$ in \S\ref{sec:bar-nilpotency}.

\subsection{Common pitfalls and how to avoid them}

\subsubsection{Pitfall 1: forgetting Koszul signs}

\emph{Wrong.} $d(a \otimes b \otimes \omega) = da \otimes b \otimes \omega + a \otimes db \otimes \omega$

\emph{Right.} $d(a \otimes b \otimes \omega) = da \otimes b \otimes \omega + (-1)^{|a|} a \otimes db \otimes \omega$

The sign $(-1)^{|a|}$ comes from moving $d$ (degree +1) past $a$ (degree $|a|$).

\subsubsection{Pitfall 2: confusing hat notations}

\emph{Wrong.} $\widehat{ij}$ could mean ``omit factors $i$ and $j$,'' or ``the set $\{i, j\}$,'' or something else entirely.

\emph{Right.} Use our convention: $\omitpair{i}{j}$ always means ``omit both $i$ and $j$'' with no ambiguity.

\subsubsection{Pitfall 3: collision divisor ordering}

\emph{Convention.} We write collision divisors with $i < j$: $\colldiv{1}{3}$ rather than $\colldiv{3}{1}$. Since $\colldiv{i}{j} = \{z_i = z_j\}$ is an unordered locus, $\colldiv{3}{1} = \colldiv{1}{3}$ (no sign). Likewise, the logarithmic forms satisfy $\LogForm{j}{i} = \LogForm{i}{j}$ since $d\log(z_j - z_i) = d\log(-(z_i - z_j)) = d\log(z_i - z_j)$.

The sign convention $e_{ji} = -e_{ij}$ applies only to Orlik--Solomon algebra generators (an algebraic convention for exterior algebra presentations), not to the geometric forms or divisors.

\subsubsection{Pitfall 4: Arnold relation orientation}

\emph{Wrong.} Assuming Arnold relations hold without signs.

\emph{Right.} The cyclic sum includes signs from wedge product antisymmetry:
\[\LogForm{1}{2} \wedge \LogForm{2}{3} + \LogForm{2}{3} \wedge \LogForm{3}{1} + \LogForm{3}{1} \wedge \LogForm{1}{2} = 0\]

Note: Each term has a $+$ sign in the cyclic sum, but the individual forms anticommute.

\subsection{Sign convention dictionary}
\label{sec:sign-dictionary-complete}

\begin{table}[ht!]
\centering
\caption{Sign conventions across sources}
\label{tab:sign-conventions-complete}
\small
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Item} & \textbf{Ours} & \textbf{BD} & \textbf{CG} & \textbf{LV} \\
\hline
\hline
Differential degree & $|d| = +1$ & implicit & $+1$ & $-1$ \\
Koszul sign rule & $(-1)^{|a||b|}$ & yes & yes & yes \\
Suspension & $s: V \to V[-1]$ & yes & yes & opposite \\
Bar complex degree & increasing & yes & yes & decreasing \\
Logarithmic 1-forms & $\eta_{ij} = \frac{dz_i - dz_j}{z_i - z_j}$ & yes & yes & N/A \\
Residue sign & $\text{Res}_{z=w}[\eta_{ij}] = +1$ & yes & yes & N/A \\
Factorization & left-to-right & yes & opposite & N/A \\
Collision divisor & $D_{ij}$ with $i < j$ & yes & same & N/A \\
Transposition & $\eta_{ji} = \eta_{ij}$ (forms) & yes & yes & N/A \\
Wedge product & $a \wedge b = (-1)^{|a||b|} b \wedge a$ & yes & yes & yes \\
Verdier duality & $\mathbb{D}(\mathcal{F}) = R\mathcal{H}om(\mathcal{F}, \omega[d])$ & yes & same & N/A \\
Central extension & $[a,b] = ab - ba$ & yes & yes & yes \\
A-infinity & $\mu_n: \mathcal{A}^{\otimes n} \to \mathcal{A}$ & implicit & yes & yes \\
\hline
\end{tabular}
\end{table}

\emph{Key to abbreviations.}
\begin{itemize}
\item BD = Beilinson--Drinfeld \cite{BD04}
\item CG = Costello--Gwilliam \cite{CG17}
\item LV = Loday--Vallette \cite{LV12}
\end{itemize}

\subsubsection{Conversion formulas}

\begin{proposition}[Loday--Vallette conversion; \ClaimStatusProvedHere]\label{prop:LV-conversion-complete}
To convert from our conventions to Loday--Vallette:
\begin{enumerate}
\item Replace $|d| = +1$ with $|d| = -1$ (flip grading direction)
\item Replace bar complex $\bar{B}^n$ with $\bar{B}_{-n}$ (decreasing filtration)
\item Keep Koszul sign rule unchanged (all four conventions agree on the Koszul sign rule)
\item Keep composition order unchanged: $(f \circ g)_{\text{LV}} = f \circ g$ (the degree reversal affects signs in the Leibniz rule, not the order of function composition)
\end{enumerate}
\end{proposition}

\begin{proof}[Verification]
The key identity is that homological grading (LV) relates to cohomological grading
(ours) by $\deg_{\text{hom}} = -\deg_{\text{coh}}$.

For a differential $d$:
\begin{itemize}
\item Our convention: $d: C^n \to C^{n+1}$, so $|d| = +1$
\item LV convention: $d: C_n \to C_{n-1}$, so $|d|_{\text{LV}} = -1$
\end{itemize}

The Koszul sign rule in the Leibniz formula is the same in both conventions:
\[d(a \otimes b) = da \otimes b + (-1)^{|a|} a \otimes db\]
(The degree $|a|$ is taken in whichever grading is active.) The sign difference between conventions manifests in the \emph{bar differential}, where LV uses explicitly suspended elements $sa$: the bar differential sign $(-1)^{|sa|} = (-1)^{|a|+1}$ in LV's homological convention (where $|sa| = |a|+1$) differs from $(-1)^{|a|}$ in ours.
\end{proof}

\subsubsection{Explicit sign calculations}

\begin{example}[Three-point Arnold relation]\label{ex:arnold-sign-explicit-dict}
For three points $z_1, z_2, z_3$, the Arnold relation is:
\[\eta_{12} \wedge \eta_{23} + \eta_{23} \wedge \eta_{31} + \eta_{31} \wedge \eta_{12} = 0\]

\emph{Sign verification.}
\begin{enumerate}
\item Each $\eta_{ij}$ has degree 1
\item Wedge product: $\eta \wedge \eta'$ has degree 2
\item Moving forms: $\eta \wedge \eta' = (-1)^{1 \cdot 1} \eta' \wedge \eta = -\eta' \wedge \eta$
\end{enumerate}

All signs are explicit and match BD conventions.
\end{example}

\begin{remark}[Fermionic vs bosonic]\label{rem:fermionic-bosonic-signs-dict}
For fermionic fields $\psi$: $\psi(z)\psi(w) = -\psi(w)\psi(z)$ (Koszul sign with $|\psi| = 1$).

For bosonic fields $\phi$: $\phi(z)\phi(w) = \phi(w)\phi(z)$ (degree $|\phi| = 0$).

The bar complex treats both uniformly via desuspension $s^{-1}: V \to V[1]$.
\end{remark}


\subsection{Master comparison table}
\label{sec:master-comparison-signs}

\begin{table}[H]
\centering
\caption{Sign conventions across four sources}
\label{tab:master-comparison-signs}
\renewcommand{\arraystretch}{1.6}
\footnotesize
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Convention} & \textbf{BD} & \textbf{CG} & \textbf{LV} & \textbf{Us} \\
\hline
\hline
\textbf{Koszul sign} & $(-1)^{|a||b|}$ & $(-1)^{|a||b|}$ & $(-1)^{|a||b|}$ & $(-1)^{|a||b|}$ \\
\hline
\textbf{Bar differential} & $d + d'$ & $d_{\text{int}} + d_{\text{ext}}$ & $d_1$ & $d_{\text{int}} + d_{\text{res}}$ \\
\hline
\textbf{Cobar degree} & $[n]$ & $[n-2]$ & $[-n]$ & $[2-n]$ \\
\hline
\textbf{Suspension} & $s: V \to V[-1]$ & $s: V \to V[-1]$ & $s: V \to V[1]$ & $s: V \to V[-1]$ \\
\hline
\textbf{Desuspension} & $s^{-1}: V \to V[1]$ & $s^{-1}: V \to V[1]$ & $s^{-1}: V \to V[-1]$ & $s^{-1}: V \to V[1]$ \\
\hline
\textbf{Twist map} & $(-1)^{|a||b|}(b \otimes a)$ & $(-1)^{|a||b|}(b \otimes a)$ & $(-1)^{|a||b|}(b \otimes a)$ & $(-1)^{|a||b|}(b \otimes a)$ \\
\hline
\textbf{Differential degree} & $+1$ & $+1$ & $-1$ & $+1$ \\
\hline
\textbf{Coalgebra comult} & $\Delta$ & $\Delta$ & $\Delta^!$ & $\Delta$ \\
\hline
\textbf{Residue orientation} & counterclockwise & contour dep. & N/A & counterclockwise \\
\hline
\textbf{$\hbar$ convention} & not used & $\hbar = 1$ & not used & $\hbar$ explicit \\
\hline
\end{tabular}
\end{table}

\subsubsection{Detailed conversion formulas}

\paragraph{Koszul signs.}

\begin{remark}[Koszul sign rule across conventions]
\label{rem:koszul-sign-all-conventions}
All four sources agree on the Koszul sign rule (Convention~\ref{conv:koszul}):
permuting graded elements $a$ and $b$ in a tensor product produces
$(-1)^{|a| \cdot |b|}$.
The apparent sign differences in bar complex formulas arise from
LV's homological grading ($|d| = -1$) and explicit suspension:
swapping $sa \otimes sb$ gives
$(-1)^{|sa||sb|} = (-1)^{(|a|+1)(|b|+1)}$, which differs from
$(-1)^{|a||b|}$ by the factor $(-1)^{|a|+|b|+1}$.
\end{remark}

\begin{example}[Koszul sign in bar construction]
For $a \in \mathcal{A}^m$, $b \in \mathcal{A}^n$, $c \in \mathcal{A}^p$:

\emph{Us/BD/CG.}
\[d(a \otimes b \otimes c) = d(a) \otimes b \otimes c + (-1)^m a \otimes d(b) \otimes c
+ (-1)^{m+n} a \otimes b \otimes d(c)\]

\emph{LV (on suspended elements $sa, sb, sc$).}
\[d(sa \otimes sb \otimes sc) = d(sa) \otimes sb \otimes sc + (-1)^{m+1} sa \otimes d(sb) \otimes sc
+ (-1)^{m+n+2} sa \otimes sb \otimes d(sc)\]

\emph{Explanation.} The sign differences arise because $|sa| = m+1$, $|sb| = n+1$, $|sc| = p+1$, and the standard Koszul rule is applied to these shifted degrees. The LV Koszul sign rule itself is the same $(-1)^{|x||y|}$.
\end{example}

\subsubsection{Quick translation table}

\begin{table}[H]
\centering
\caption{Translation formulas between conventions}
\begin{tabular}{|l|c|}
\hline
\textbf{To convert from} & \textbf{Apply this transformation} \\
\hline
\hline
LV $\to$ Us/BD/CG & Multiply internal terms by $(-1)^{|a|}$, add chiral product \\
\hline
CG $\to$ Us & Shift notation: CG's $V[1]$ (convention $V[n]^k = V^{k-n}$) equals our $V[-1]$ \\
\hline
BD $\to$ Us & Split $d''$ into $d_{\text{residue}}$ and $d_{\text{correction}}$ \\
\hline
Us $\to$ BD & Combine $d_{\text{residue}} + d_{\text{correction}}$ into $d''$ \\
\hline
Us $\to$ LV & Remove chiral product, multiply by $(-1)^{|a|}$ \\
\hline
\end{tabular}
\end{table}

\subsubsection{Recommendations for readers}

\begin{itemize}
\item \emph{Reading BD.} Our conventions match closely; main difference is we separate out
quantum corrections explicitly.
\item \emph{Reading CG.} The conventions match exactly; use their formulas directly.
\item \emph{Reading LV.} Add extra $(-1)^{|a|}$ signs and remember to include chiral product
which LV does not have.
\end{itemize}


%% ======================================================================
%% Multi-source convention translations: formula-level details
%% ======================================================================

\section{Multi-source convention translations}
\label{sec:multi-source-translations}

The dictionary in \S\ref{app:sign-conventions} records which conventions differ.
This section gives \emph{formula-level} translations: for each key algebraic
object central to this monograph, we write the defining equation in each
convention and exhibit the explicit sign mismatch. Following the
Chriss--Ginzburg principle, special attention is paid to Maurer--Cartan
elements, convolution dg~Lie algebras, and the bar-cobar constructions that
carry them.

\subsection{Loday--Vallette $\leftrightarrow$ this manuscript: bar-cobar formulas}
\label{sec:lv-us-formulas}

\subsubsection{Bar differential on desuspended generators}

The bar complex of an augmented dg algebra $(\cA, d, \mu)$ is built on
$T^c(s^{-1}\bar{\cA})$. Write $[a_1|\cdots|a_n] := s^{-1}a_1\otimes\cdots\otimes s^{-1}a_n$
with $|s^{-1}a_i| = |a_i| - 1$.

\emph{Our convention} (cohomological, $|d|=+1$, desuspension in bar).
\begin{equation}\label{eq:bar-diff-us}
d_{\mathrm{bar}}[a_1|\cdots|a_n]
= \sum_{i=1}^{n-1} (-1)^{\sum_{j=1}^{i}(|a_j|-1)}\,
 [a_1|\cdots|a_i \cdot a_{i+1}|\cdots|a_n]
\;+\; \text{(internal $d$-terms)}.
\end{equation}

\emph{Loday--Vallette convention} (homological, $|d|=-1$, suspension in bar).
LV writes the bar complex on $T^c(s\bar{\cA})$ with $|sa_i| = |a_i|+1$.
Their bar differential is:
\begin{equation}\label{eq:bar-diff-lv}
d_1(sa_1\otimes\cdots\otimes sa_n)
= \sum_{i=1}^{n-1} (-1)^{\sum_{j=1}^{i}|sa_j|}\,
 sa_1\otimes\cdots\otimes s(a_i \cdot a_{i+1})\otimes\cdots\otimes sa_n.
\end{equation}

\emph{Translation.} Identifying $s^{-1}a$ (us) with $sa$ (LV) under the
relabeling $\deg_{\mathrm{coh}} = -\deg_{\mathrm{hom}}$, the exponents
$\sum_{j\leq i}(|a_j|-1)$ in~\eqref{eq:bar-diff-us} become
$\sum_{j\leq i}|sa_j|$ in~\eqref{eq:bar-diff-lv} because
$|a_j|-1 = |a_j| + 1 = |sa_j|$ after negating the grading.
The two formulas are \emph{identical} as linear maps; only the bookkeeping changes.

\begin{example}[Explicit sign: two generators of odd degree]
Let $a, b \in \cA^1$ (cohomological degree~1). Then $|s^{-1}a| = 0$,
$|s^{-1}b| = 0$.
\begin{align*}
\text{Us:} &\quad d_{\mathrm{bar}}[a|b]
 = (-1)^{|a|-1}[a\cdot b] = (-1)^{0}[ab] = [ab]. \\
\text{LV:} &\quad d_1(sa\otimes sb)
 = (-1)^{|sa|}s(ab) = (-1)^{2}s(ab) = s(ab).
\end{align*}
Both give the unsigned product; the apparent sign $(-1)^2 = +1$ in LV
matches $(-1)^0 = +1$ in ours.

Now let $a \in \cA^0$, $b \in \cA^1$:
\begin{align*}
\text{Us:} &\quad d_{\mathrm{bar}}[a|b]
 = (-1)^{|a|-1}[ab] = (-1)^{-1}[ab] = -[ab]. \\
\text{LV:} &\quad d_1(sa\otimes sb)
 = (-1)^{|sa|}s(ab) = (-1)^{1}s(ab) = -s(ab).
\end{align*}
Both produce a minus sign. The exponent looks different ($-1$ vs.\ $1$),
but the sign is the same: $(-1)^{-1} = (-1)^1 = -1$.
\end{example}

\subsubsection{Cobar differential and $A_\infty$ structure maps}

The cobar differential on $\Omega(C) = T(s^{-1}\bar{C})$ for a dg coalgebra $(C, d, \Delta)$ is:
\[
d_\Omega(s^{-1}c) = -s^{-1}(dc)
 - \sum_{(c)} (-1)^{|c'|}\, (s^{-1}c') \otimes (s^{-1}c'').
\]
The \emph{minus sign} on $s^{-1}(dc)$ arises from the desuspended differential
(Proposition~\ref{prop:susp-diff}). The minus sign on the comultiplication
term is specific to the manuscript's convention
$b_2(s^{-1}a,s^{-1}b) = (-1)^{|a|}s^{-1}(ab)$
(desuspension for bar, Computation~\ref{comp:bar-signs-2-1});
in the Loday--Vallette convention~\cite[\S2.2]{LV12}, where the bar uses
suspension~$s$ and $b_2(sa,sb) = (-1)^{|a|+1}s(ab)$, the comultiplication
term carries a plus sign instead. The relative sign between the two terms
is fixed by the bar-cobar adjunction: the counit
$\varepsilon\colon \Omega(\bar B(A)) \to A$ is a chain map only with
matching signs on both terms
(see Computation~\ref{comp:cobar-signs-1-2} and
equation~\eqref{eq:cobar-diff-generators}).

\subsubsection{$A_\infty$ relations}

For an $A_\infty$-algebra $(A, \{m_n\}_{n\geq 0})$:

\emph{Our convention.}
\begin{equation}\label{eq:ainf-us}
\sum_{\substack{r+s+t = n \\ r,t \geq 0,\; s \geq 1}}
 (-1)^{rs + t}\, m_{r+1+t}(a_1,\ldots,a_r, m_s(a_{r+1},\ldots,a_{r+s}), a_{r+s+1},\ldots,a_n) = 0.
\end{equation}

\emph{LV convention.} LV defines the desuspended structure maps
$b_n := s \circ m_n \circ (s^{-1})^{\otimes n}$.
The $A_\infty$ relation on the $b_n$ reads:
\[
\sum_{r+s+t=n} (-1)^{rs+t}\, b_{r+1+t} \circ (\mathrm{id}^{\otimes r} \otimes b_s \otimes \mathrm{id}^{\otimes t}) = 0,
\]
which is identical to~\eqref{eq:ainf-us}: the sign $(-1)^{rs+t}$ is the same in both conventions.

\emph{Curved case.} When $m_0 \neq 0$, the $A_\infty$ relation at $n=1$ becomes
$m_1^2(a) = m_2(m_0, a) - m_2(a, m_0) = [m_0, a]$ (commutator with the curving element).
Both conventions agree: the sign is a \emph{commutator}, not an anticommutator.

\subsection{Beilinson--Drinfeld $\leftrightarrow$ this manuscript: chiral operations}
\label{sec:bd-us-formulas}

\subsubsection{Chiral product vs.\ OPE residue}

BD define the chiral product via the $!$-pushforward along the diagonal:
\[
\mu^{\mathrm{ch}}_{\mathrm{BD}}: j_*j^*(\cA \boxtimes \cA) \longrightarrow \Delta_! \cA
\]
where $j: X^2 \setminus \Delta \hookrightarrow X^2$ and $\Delta: X \hookrightarrow X^2$.

Our convention makes the residue explicit:
\[
\mu^{\mathrm{ch}}_{\mathrm{us}}(a \otimes b) = \Res_{z=w}\Bigl[\frac{a(z) \otimes b(w)}{z - w}\Bigr] dz.
\]

\emph{Translation.} BD's $\mu^{\mathrm{ch}}$ encodes all OPE poles simultaneously;
our $\mu^{\mathrm{ch}}$ extracts only the first-order pole. The sign agreement
is exact: both use counterclockwise residue orientation. The key difference
is that BD's formulation is intrinsically coordinate-free (D-module language),
while ours uses the local coordinate $z - w$ to make signs visible.

\begin{example}[Heisenberg at 2 points]
For the Heisenberg algebra $\cH$ with OPE $b(z)c(w) \sim 1/(z-w)$:

\emph{BD:} $\mu^{\mathrm{ch}}(b \boxtimes c) = \mathbf{1} \in \Delta_!\cH$.

\emph{Us:} $\Res_{z=w}[b(z) \otimes c(w) \cdot \eta_{12}] = \mathbf{1}$
where $\eta_{12} = d\log(z_1 - z_2)$.

Both give $+\mathbf{1}$ (no sign).
Now reverse the order:

\emph{BD:} $\mu^{\mathrm{ch}}(c \boxtimes b)$; the chiral product is \emph{not}
graded-commutative; BD's skew-commutativity axiom gives
$\mu^{\mathrm{ch}}(c \boxtimes b) = -(-1)^{|b||c|}\mu^{\mathrm{ch}}(b \boxtimes c) = -\mathbf{1}$
(since $|b| = |c| = 0$).

\emph{Us:} $\Res_{z=w}[c(z) \otimes b(w) \cdot \eta_{12}] = -\mathbf{1}$
from $c(z)b(w) \sim -1/(z-w)$.

Both agree: $-\mathbf{1}$.
\end{example}

\subsubsection{Factorization and the bar complex}

BD's factorization axiom on disjoint opens $U_1 \sqcup U_2 \subset X$:
\[
\cA^{\mathrm{fact}}_{\mathrm{BD}}(U_1 \sqcup U_2) \xrightarrow{\;\sim\;} \cA^{\mathrm{fact}}_{\mathrm{BD}}(U_1) \otimes \cA^{\mathrm{fact}}_{\mathrm{BD}}(U_2).
\]

Our version as a bar complex splitting:
\[
\bar{B}_*(\cA)|_{U_1 \sqcup U_2} \xrightarrow{\;\sim\;} \bar{B}_*(\cA)|_{U_1} \otimes \bar{B}_*(\cA)|_{U_2}.
\]

The isomorphism is the same linear map; our presentation makes explicit the
\emph{coassociativity sign} in the splitting. For elements
$[a_1|\cdots|a_n]$ splitting as $[a_1|\cdots|a_k] \otimes [a_{k+1}|\cdots|a_n]$,
the sign is $(-1)^{(\sum_{i\leq k}|s^{-1}a_i|)(\sum_{j>k}|s^{-1}a_j|)}$
from the Koszul rule on desuspended elements. BD absorb this sign into the
D-module structure.

\subsection{Costello--Gwilliam $\leftrightarrow$ this manuscript: BV and genus}
\label{sec:cg-us-formulas}

\subsubsection{Quantum master equation}

CG's BV formalism (on a manifold $M$ of dimension $d$) uses the quantum
master equation (QME):
\begin{equation}\label{eq:qme-cg}
\hbar \Delta_{\BV} S + \tfrac{1}{2}\{S, S\}_{\BV} = 0
\end{equation}
where $\Delta_{\BV}$ is the BV Laplacian, $\{-,-\}_{\BV}$ is the BV antibracket,
and $S$ is the action functional.

\emph{Our convention} (specialized to curves, $d=1$): the QME becomes the
Maurer--Cartan equation in the modular convolution algebra
$\mathfrak{g}^{\mathrm{mod}}_\cA$:
\begin{equation}\label{eq:mc-us}
D_\cA \Theta_\cA + \tfrac{1}{2}[\Theta_\cA, \Theta_\cA] = 0
\end{equation}
where $D_\cA$ is the convolution differential and $[-,-]$ is the dg Lie bracket
on $\Convstr(C^!_{\mathrm{ch}}, P^{\mathrm{ch}})$.

\emph{Translation.}
\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{CG} & \textbf{Us} \\
\hline
$\hbar \Delta_{\BV}$ & $D_\cA$ (convolution differential) \\
$\{-,-\}_{\BV}$ & $[-,-]$ (dg Lie bracket on $\Convstr$) \\
$S$ (action functional) & $\Theta_\cA$ (MC element) \\
Loop order $\ell$ & Genus $g$ \\
$\hbar^\ell$ (loop expansion) & Genus filtration on $\Theta_\cA^{\leq r}$ \\
\hline
\end{tabular}
\end{center}

The factor $\frac{1}{2}$ is present in \emph{both} conventions; this is a
common source of error. Omitting it leads to incorrect signs in the
obstruction theory (cf.\ Pitfall~8 in \S\ref{sec:chiral-pitfalls}).

\subsubsection{BV bracket vs.\ bar differential}

CG's BV antibracket on a curve $X$, applied to local functionals $F, G$:
\[
\{F, G\}_{\mathrm{CG}} = \int_X \frac{\delta F}{\delta \phi(z)} \frac{\delta G}{\delta \phi^+(z)}\, dz
 \;-\; (-1)^{|F||G|} \int_X \frac{\delta G}{\delta \phi(z)} \frac{\delta F}{\delta \phi^+(z)}\, dz.
\]

Our bar differential encodes the same data geometrically:
\[
d_{\mathrm{res}}[a|b] = (-1)^{|a|-1}\, [a \cdot b]
\]
where $a \cdot b$ is the chiral product (residue of the OPE).

\emph{Translation.} CG's antibracket restricted to 2-point functionals on a
curve reproduces our bar differential. The sign $(-1)^{|F||G|}$ in CG
becomes $(-1)^{|a|-1}$ in ours because the desuspension shifts degrees:
$|s^{-1}a| = |a| - 1$, so $|F| = |s^{-1}a| = |a| - 1$.

\subsubsection{Renormalization and completion}

CG's renormalization group flow (from scale $\Lambda$ to scale $\Lambda'$):
\[
I[\Lambda'] = W(P(\Lambda', \Lambda), I[\Lambda])
\]
where $W$ is the Feynman diagram sum and $P(\Lambda',\Lambda)$ is the propagator.

Our analogue: the nilpotent completion of the bar complex
$\hat{B}(\cA) = \varprojlim_N B(\cA)/F^N$ with the completion filtration.

There is no sign discrepancy here; the relationship is structural rather
than sign-dependent. The key identification is:
\[
\text{CG's $\ell$-loop Feynman graph} \;\longleftrightarrow\;
\text{our genus-$\ell$ stratum of }\bar{B}^{(g,n)}_*(\cA).
\]

\subsection{Kontsevich $\leftrightarrow$ this manuscript: graph complexes and formality}
\label{sec:kont-us-formulas}

\subsubsection{Propagator conventions}

Kontsevich's propagator on $\mathbb{R}^2$ (identified with $\mathbb{C}$):
\[
\omega_K(z, w) = \frac{1}{2\pi i} d\arg(z - w)
 = \frac{1}{2\pi i} \frac{d\bar{z} - d\bar{w}}{z - w}.
\]

Our propagator on a curve $X$:
\[
\omega_{\mathrm{us}}(z, w) = \eta_{zw} = d\log(z - w) = \frac{dz - dw}{z - w}.
\]

\emph{Translation.} Our propagator is the \emph{holomorphic part} of
Kontsevich's; the antiholomorphic part $d\bar{z}$ drops out on curves
(where the relevant forms are algebraic/holomorphic). The factor
$1/(2\pi i)$ in Kontsevich accounts for the residue normalization;
we absorb it into the residue map $\Res_{z=w}[\cdots] = +1$.

\begin{example}[Graph weight: single edge]
Consider a graph $\Gamma$ with two external vertices $1, 2$ and one
internal edge connecting them.

\emph{Kontsevich:}
$w_\Gamma = \int_{C_2(\mathbb{R}^2)} \omega_K(z_1, z_2) = \frac{1}{2\pi i}
\int d\arg(z_1 - z_2) = 1.$

\emph{Us:}
$w_\Gamma = \Res_{z_1 = z_2}[\eta_{12}] = +1.$

Both give $+1$, confirming the propagator normalization is consistent.
\end{example}

\subsubsection{Graph orientations and genus stratification}

Kontsevich's graph complex uses \emph{directed} graphs with edge orientations
producing signs $(-1)^{\text{number of edge reversals}}$. Our genus-stratified
graphs carry:
\begin{enumerate}[label=(\roman*)]
\item \emph{Vertex ordering}: lexicographic ($v_1 < v_2 < \cdots$), producing
signs from $\Det(\{v_1,\ldots,v_n\})$.
\item \emph{Edge orientation}: from the ordering of collision divisors
$D_{ij}$ with $i < j$, reproducing Kontsevich's edge signs.
\item \emph{Genus labels}: absent in Kontsevich (genus 0 only), present in
our stable-graph coefficient algebra $\mathcal{G}_{\mathrm{st}}$.
\end{enumerate}

\emph{Translation at genus 0.} Kontsevich's directed graph $\Gamma$
with $n$ vertices corresponds to our genus-0 graph $(\Gamma, g \equiv 0)$
in $\mathcal{G}_{\mathrm{st}}^{(0,n)}$. The edge-orientation signs agree:
reversing edge $(i,j)$ to $(j,i)$ gives $(-1)$ in both conventions.

\emph{Beyond genus 0.} Kontsevich's ``wheel'' graphs (graphs with cycles)
produce contributions that in our framework are identified with
\emph{higher-genus} terms. A wheel with $k$ edges corresponds to a
genus contribution at $g = 1$ (for a single cycle) or higher, absorbed
into the modular bar complex $\bar{B}^{(g,n)}(\cA)$.


%% ======================================================================
%% Extended master comparison table
%% ======================================================================

\section{Extended master comparison table}
\label{sec:extended-master-comparison}

The tables in \S\S\ref{sec:master-comparison-signs}--\ref{sec:sign-dictionary-complete}
record sign conventions for basic operations. The following table extends the
comparison to the \emph{algebraic structures} central to this monograph: MC~elements,
convolution algebras, curvature, and the shadow obstruction tower.

\begin{table}[H]
\centering
\caption{Convention comparison for algebraic structures}
\label{tab:algebraic-structures-comparison}
\renewcommand{\arraystretch}{1.5}
\footnotesize
\begin{tabular}{|>{\raggedright\arraybackslash}p{3.6cm}|>{\raggedright\arraybackslash}p{2.5cm}|>{\raggedright\arraybackslash}p{2.5cm}|>{\raggedright\arraybackslash}p{2.2cm}|>{\raggedright\arraybackslash}p{2.5cm}|}
\hline
\textbf{Structure} & \textbf{BD} & \textbf{CG} & \textbf{LV} & \textbf{Us} \\
\hline
\hline
MC equation & N/A & $\hbar\Delta S + \frac{1}{2}\{S,S\}=0$ & $d\alpha + \frac{1}{2}[\alpha,\alpha]=0$ & $D\Theta + \frac{1}{2}[\Theta,\Theta]=0$ \\
\hline
Convolution Lie bracket & implicit & $\{-,-\}_{\BV}$ & $[-,-]_{\mathrm{pre}}$ & $[-,-]_{\Convstr}$ \\
\hline
Curvature & implicit & $F_\nabla = d\nabla + \nabla^2$ & $m_0$ & $\kappa(\cA)$ \\
\hline
Curved $A_\infty$ relation & N/A & $m_1^2 = [m_0,-]$ & $m_1^2 = [m_0,-]$ & $m_1^2(a)=[m_0,a]$ \\
\hline
$\hbar$ parameter & N/A & explicit & N/A & genus filtration \\
\hline
Bar-cobar adjunction & factorization axiom & descent & $B \dashv \Omega$ & $\bar{B} \dashv \Omega$ \\
\hline
Koszul dual & not discussed & not discussed & $\cP^!$ & $\cA^!$ \\
\hline
Shadow obstruction tower & N/A & N/A & N/A & $\Theta_\cA^{\leq r}$ \\
\hline
Modular operad action & N/A & graph complex & N/A & $\mathrm{FCom}$-algebra \\
\hline
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Convention comparison for geometric operations on curves}
\label{tab:geometric-operations-comparison}
\renewcommand{\arraystretch}{1.5}
\footnotesize
\begin{tabular}{|>{\raggedright\arraybackslash}p{3.6cm}|>{\raggedright\arraybackslash}p{2.5cm}|>{\raggedright\arraybackslash}p{2.5cm}|>{\raggedright\arraybackslash}p{2.2cm}|>{\raggedright\arraybackslash}p{2.5cm}|}
\hline
\textbf{Operation} & \textbf{BD} & \textbf{CG} & \textbf{Kontsevich} & \textbf{Us} \\
\hline
\hline
Propagator & implicit in $j_*j^*$ & $P_\epsilon$ (regularized) & $\frac{1}{2\pi i}d\arg$ & $d\log(z-w)$ \\
\hline
Residue normalization & $+1$ & contour dep.\ & $(2\pi i)^{-1}$ & $+1$ \\
\hline
Configuration compactification & $\mathrm{Ran}(X)$ & FM (real) & $C_n(\mathbb{R}^d)$ (open) & $\FM_n(X)$ (algebraic) \\
\hline
Genus parameter & N/A & loop order $\ell$ & N/A & $g$ \\
\hline
Boundary structure & factorization isom.\ & codim-1 strata & boundary forms & collision divisors $D_T$ \\
\hline
Verdier duality & $\mathbb{D} = R\mathcal{H}om(-,\omega[1])$ & Serre duality & Poincar\'e duality & $\mathbb{D} = R\mathcal{H}om(-,\omega[1])$ \\
\hline
OPE & $\cA(\Delta)$ & observables on disk & N/A & $a(z)b(w) \sim \sum \frac{c_n(w)}{(z-w)^n}$ \\
\hline
\end{tabular}
\end{table}

\begin{remark}[Reading the table]
An entry ``N/A'' means the structure is not discussed in that source,
not that it cannot be formulated there. For instance, LV do not discuss
Maurer--Cartan elements in the chiral setting, but one can define them in
LV's framework by working on the operadic bar-cobar level; the MC equation
$d\alpha + \frac{1}{2}[\alpha,\alpha] = 0$ in the LV column refers to
the general operadic MC equation with homological signs.
\end{remark}


%% ======================================================================
%% Common pitfalls in chiral computations
%% ======================================================================

\section{Common pitfalls in chiral computations}
\label{sec:chiral-pitfalls}

The pitfalls in \S\ref{sec:sign-dictionary-complete} concern general sign
errors. This section collects pitfalls specific to \emph{chiral algebra}
computations, errors that arise from the interaction of algebraic signs with
geometric residues, OPE poles, and the modular structure.

\subsection{Pitfall 5: Sugawara signs at the critical level}

\emph{Wrong.} ``The Sugawara central charge diverges at $k = -h^\vee$.''

\emph{Right.} The Sugawara construction is \emph{undefined} at the critical
level $k = -h^\vee$: the denominator $k + h^\vee$ appears in the definition
of the Sugawara tensor $S(z) = \frac{1}{2(k+h^\vee)} \sum_a {:}J^a(z)J_a(z){:}$,
not merely in the central charge formula.

\emph{Sign consequence.} The Feigin--Frenkel duality $k \leftrightarrow -k - 2h^\vee$
fixes $k = -h^\vee$ and interchanges the two ``halves'' of the critical level.
This duality reverses the sign of $k + h^\vee$:
\[
k \;\longmapsto\; -k - 2h^\vee
\quad\Longrightarrow\quad
(k + h^\vee) \;\longmapsto\; -(k + h^\vee).
\]
Any formula involving $(k + h^\vee)^{-1}$ therefore picks up a sign under
Feigin--Frenkel duality. This sign must be tracked through the Koszul dual:
the affine algebra $\hat{\mathfrak{g}}_k$ at level $k$ has Koszul dual
at level $-k - 2h^\vee$, and the curvature $\kappa(\hat{\mathfrak{g}}_k)$
transforms accordingly.

\subsection{Pitfall 6: Virasoro self-duality point}

\emph{Wrong.} ``The Virasoro algebra is self-dual at $c = 26$.''

\emph{Right.} $\mathrm{Vir}_c^! = \mathrm{Vir}_{26 - c}$, so self-duality
requires $c = 26 - c$, i.e., $c = 13$. The value $c = 26$ is where the
Koszul dual has $c^! = 0$, not where self-duality holds.

\emph{Sign consequence.} The shadow obstruction tower's quartic contact invariant
$Q^{\mathrm{contact}}_{\mathrm{Vir}} = 10/[c(5c+22)]$ has poles at $c = 0$
and $c = -22/5$. Under $c \mapsto 26 - c$, this transforms as:
\[
Q^{\mathrm{contact}}_{\mathrm{Vir}^!}
= \frac{10}{(26-c)(5(26-c)+22)}
= \frac{10}{(26-c)(152-5c)}.
\]
At the self-dual point $c = 13$: $Q = 10/[13 \cdot 87] = 10/1131$.
At $c = 26$: $Q = 10/[26 \cdot 152] = 10/3952$, which is
\emph{not} the value at $c^! = 0$ (where $Q$ diverges).

\subsection{Pitfall 7: Orlik--Solomon vs.\ differential form signs}

\emph{Wrong.} Assuming $\eta_{ji} = -\eta_{ij}$ as differential forms.

\emph{Right.} The logarithmic 1-forms satisfy
$\eta_{ji} = d\log(z_j - z_i) = d\log(-(z_i - z_j)) = d\log(z_i - z_j) = \eta_{ij}$
because $d\log(-1) = 0$. However, the Orlik--Solomon \emph{algebra generators}
$e_{ij}$ satisfy $e_{ji} = -e_{ij}$ by convention (exterior algebra presentation).

\emph{Sign consequence.} Confusing the two leads to a global sign error
in the bar differential. Consider the Arnold relation:
\begin{align*}
\text{As forms:} &\quad \eta_{12}\wedge\eta_{23} + \eta_{23}\wedge\eta_{31} + \eta_{31}\wedge\eta_{12} = 0. \\
\text{As OS generators:} &\quad e_{12}\wedge e_{23} + e_{23}\wedge e_{31} + e_{31}\wedge e_{12} = 0
\end{align*}
These are the \emph{same} equation because $\eta_{31} = \eta_{13}$ (forms)
but $e_{31} = -e_{13}$ (OS). Substituting $e_{31} = -e_{13}$ gives:
\[
e_{12}\wedge e_{23} - e_{23}\wedge e_{13} - e_{13}\wedge e_{12} = 0
\]
which, using $e_{ij}\wedge e_{kl} = -e_{kl}\wedge e_{ij}$, simplifies to
$e_{12}\wedge e_{23} + e_{13}\wedge e_{23} - e_{13}\wedge e_{12} = 0$.
Both forms are correct; the danger is in mixing the conventions within a
single computation.

\subsection{Pitfall 8: the factor of $\frac{1}{2}$ in the MC equation}

\emph{Wrong.} Writing the MC equation as $D\Theta + [\Theta, \Theta] = 0$.

\emph{Right.} $D\Theta + \frac{1}{2}[\Theta, \Theta] = 0$.

\emph{Sign consequence.} The factor $\frac{1}{2}$ arises because the
Lie bracket $[-,-]$ is antisymmetric: $[\Theta, \Theta] = -(-1)^{|\Theta|^2}[\Theta, \Theta]$.
For $|\Theta|$ odd (as in a shifted Lie algebra), $[\Theta,\Theta] \neq 0$
in general, and the $\frac{1}{2}$ is essential.

Concretely, the MC equation for the shadow obstruction tower element $\Theta_\cA^{\leq 2} = \kappa(\cA)$ gives:
\[
D\kappa + \tfrac{1}{2}[\kappa, \kappa] = o^{(3)}(\cA)
\]
where $o^{(3)}$ is the cubic obstruction class. Without the $\frac{1}{2}$,
the obstruction class would be off by a factor of~2, propagating errors
into all higher shadow computations.

Similarly, the QME in CG's convention~\eqref{eq:qme-cg}:
$\hbar\Delta S + \frac{1}{2}\{S,S\} = 0$. Omitting the $\frac{1}{2}$
from the antibracket term doubles the classical BV cohomology obstruction.

\subsection{Pitfall 9: suspension in the Koszul dual}

\emph{Wrong.} ``$\mathrm{Com}^! = \mathrm{coLie}$.''

\emph{Right.} $\mathrm{Com}^! = \mathrm{Lie}$. The Koszul dual \emph{operad}
(not cooperad) of $\mathrm{Com}$ is $\mathrm{Lie}$.

\emph{Sign consequence.} The operadic Koszul duality involves an operadic
suspension $\fS$ (Definition~\ref{def:susp-operadic}):
\[
\cP^{\scriptstyle \text{\textexclamdown}} = (\fS^{-1}\cP^!)^\vee, \qquad
\fS\cP(n) = \sgn_n \otimes \cP(n)[n-1].
\]
The sign representation $\sgn_n$ is the source of the
Lie $\leftrightarrow$ Com duality: $\mathrm{Com}(n) = k$ (trivial representation),
and $\fS^{-1}\mathrm{Lie}(n) = \sgn_n \otimes \mathrm{Lie}(n)[1-n]$.
Omitting the operadic suspension yields $\mathrm{coLie}$ instead of $\mathrm{Lie}$,
which changes the sign of the bracket in all convolution algebra computations.

\subsection{Pitfall 10: FM compactification vs.\ complement of diagonal}

\emph{Wrong.} ``The Fulton--MacPherson space is $X^n \setminus \bigcup_{i<j}\Delta_{ij}$.''

\emph{Right.} $\FM_n(X)$ is obtained by \emph{blowing up} along diagonals (in order
of increasing codimension), not by removing them. The result is a smooth
compact variety containing the configuration space as an open dense subset.

\emph{Sign consequence.} Residues along boundary divisors of $\FM_n(X)$ use
the \emph{normal bundle orientation} of the exceptional divisor, not the
restriction to a deleted neighborhood. For curves, the exceptional divisor
$E_{ij} \cong \mathbb{P}(T_{z_i}X)$ is a point (Construction~\ref{constr:sign-blowup}),
so no additional sign arises. But for higher-dimensional varieties,
confusing the complement with the blowup introduces orientation errors
in every residue computation.

\subsection{Pitfall 11: prime form and spinor signs}

\emph{Wrong.} ``The prime form $E(z,w)$ is a section of $K^{1/2} \boxtimes K^{1/2}$.''

\emph{Right.} $E(z,w)$ is a section of $K^{-1/2} \boxtimes K^{-1/2}$
(negative half-powers of the canonical bundle).

\emph{Sign consequence.} The prime form satisfies $E(z,w) = -E(w,z)$
(antisymmetric). Confusing $K^{1/2}$ with $K^{-1/2}$ reverses the
sign of the genus-$g$ propagator:
\[
\omega_g(z,w) = d_z d_w \log E(z,w) = \text{Bergman kernel}
\]
and introduces a global sign error in the higher-genus bar complex
$\bar{B}^{(g,n)}(\cA)$ for $g \geq 1$.

\subsection{Pitfall 12: the Borcherds identity and $d^2$}

The Borcherds bracket-differential satisfies $d_{\mathrm{bracket}}^2 \neq 0$
in general (this is proved for all $2^{11} = 2048$ sign choices; see
\S\ref{sec:bar-nilpotency}). Nilpotency $d^2 = 0$ requires the
\emph{full} Borcherds differential, which includes both the bracket term
and the internal differential. Forgetting the internal differential, a
common error when translating from LV's purely algebraic setting to our
geometric one, breaks $d^2 = 0$.

\emph{Explicit example.} For the affine algebra $\hat{\mathfrak{sl}}_2$ at level $k$,
the bar differential has:
\[
d^2[e|f|h] = d\bigl((-1)^0[ef|h] - (-1)^0[e|fh]\bigr)
 = [ef \cdot h] - [e \cdot fh] - [ef \cdot h] + [e \cdot fh] = 0
\]
using both the bracket (residue) part and the internal differential.
Omitting either part generically gives $d^2 \neq 0$.

\subsection{Summary of chiral pitfalls}

\begin{center}
\begin{tabular}{|c|l|l|}
\hline
\textbf{\#} & \textbf{Pitfall} & \textbf{Consequence if ignored} \\
\hline
5 & Sugawara undefined at $k=-h^\vee$ & Wrong Feigin--Frenkel signs \\
6 & Vir self-dual at $c=13$ (not 26) & Wrong shadow invariant values \\
7 & $\eta_{ji} = \eta_{ij}$ (forms) vs.\ $e_{ji} = -e_{ij}$ (OS) & Global sign in bar differential \\
8 & Factor $\frac{1}{2}$ in MC equation & Obstruction class off by 2 \\
9 & $\mathrm{Com}^! = \mathrm{Lie}$ (not $\mathrm{coLie}$) & Wrong bracket sign in $\Convstr$ \\
10 & FM = blowup (not complement) & Orientation errors in residues \\
11 & Prime form: $K^{-1/2}$ (not $K^{+1/2}$) & Wrong genus-$g$ propagator sign \\
12 & $d_{\mathrm{bracket}}^2 \neq 0$ & Need full Borcherds $d$ for $d^2=0$ \\
\hline
\end{tabular}
\end{center}

\begin{remark}[Signs as a diagnostic tool]
When a computation produces an unexpected sign, it is almost always one of
the twelve pitfalls above (or their combination). A useful debugging strategy:
first verify the computation in the Heisenberg algebra (where all generators
have degree~0 and all Koszul signs are trivial), then reintroduce grading.
If the Heisenberg case already fails, the error is geometric (Pitfalls~7,
10, 11); if it only appears with grading, the error is algebraic (Pitfalls~5,
6, 8, 9, 12).
\end{remark}
