%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CHAPTER 68: DEFORMATION QUANTIZATION EXAMPLES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Deformation quantization examples}
\label{chap:deformation-examples}

The preceding chapter established the chiral Kontsevich formality theorem in the abstract; this chapter works out its consequences for specific examples.  We construct $\Pinf$-chiral structures (the semiclassical objects), compute their quantizations (the $\Eone$-chiral deformations), and verify the bar-cobar predictions in each case.  The examples range from Coisson algebras (Poisson vertex algebras, the commutative starting point) through star products on lattice vertex algebras to symplectic fermion deformations, illustrating the full hierarchy $\mathrm{Coisson} \to \Einf \to \Eone$.

\section{\texorpdfstring{$\Pinf$ structures}{Pinf structures}}
\label{sec:pinf-structures}
\begin{definition}[$\Pinf$-chiral algebra]\label{def:pinf-chiral-detailed}
A \emph{$\Pinf$-chiral algebra} (Definition~\ref{def:pinf-chiral}) carries
\emph{two} compatible chiral-operad structures:
\begin{enumerate}[label=(\roman*)]
\item A $\chirCom$-algebra structure: commutative chiral product (i.e.\
  an $\Einf$-chiral algebra / vertex algebra).
\item A $\chirLie$-algebra structure: chiral Lie bracket $\{-, -\}$.
\item Leibniz compatibility: $\{a, b \cdot c\} = \{a, b\} \cdot c + b \cdot \{a, c\}$.
\end{enumerate}
Since ${\chirCom}^! \cong \chirLie$, the two chiral structures are
presented across Koszul dual frames.
Equivalently, $\mathcal{A}$ is an algebra over the chiral Poisson operad
$\chirPois = \chirCom \circ \chirLie$.

This is fundamentally different from a coisson algebra
(Definition~\ref{def:coisson}), which has only a \emph{single}
$\lambda$-bracket on a commutative (non-chiral) $\mathcal{D}$-module.
A $\Pinf$-chiral algebra has two full chiral operations; a coisson algebra
has none.
\end{definition}

\begin{example}[Classical affine Poisson]\label{ex:classical-affine}
Let $\mathfrak{g}^*$ be the dual of a Lie algebra with Kirillov--Kostant Poisson structure:
\[
\{f, g\}(x) = x([df_x, dg_x])
\]
The loop algebra version $L\mathfrak{g}^* = \mathfrak{g}^* \otimes \bC[t, t^{-1}]$ has a
coisson (PVA) structure:
\[
\{J^a_\lambda J^b\} = f^{ab}_c J^c
\]
This is the classical limit ($k \to \infty$) of the Kac--Moody vertex algebra;
its deformation quantization produces $\hat{\mathfrak{g}}_k$ as an $\Einf$-chiral
algebra.
\end{example}


\subsection{Coisson algebras}

\begin{definition}[Coisson algebra]\label{def:coisson}
\index{coisson algebra|textbf}
A \emph{coisson algebra} (Beilinson--Drinfeld \cite{BD04}) is a commutative
$\mathcal{D}_X$-algebra $\mathcal{A}$ equipped with a Lie$^*$ bracket
$\{-,-\}\colon \mathcal{A} \boxtimes \mathcal{A} \to \Delta_* \mathcal{A}$
satisfying the Leibniz rule with respect to the commutative product.
Equivalently, $\mathcal{A}$ is a Poisson vertex algebra (PVA): a commutative
differential algebra with a $\lambda$-bracket $\{a_\lambda b\}$ satisfying
sesquilinearity, skew-symmetry, Jacobi, and Leibniz.

A coisson algebra is \emph{not} a chiral algebra: it carries no OPE, only a
commutative product and a compatible bracket encoding the singular part of a
would-be OPE.  Coisson algebras are the semiclassical limits of vertex algebras
($\Einf$-chiral algebras).
\end{definition}

\begin{remark}[Coisson algebras and the chiral hierarchy]
\label{rem:coisson-chiralhierarchy}
The distinction between coisson algebras and $\Pinf$-chiral algebras
(Definition~\ref{def:pinf-chiral}) is fundamental:
\begin{itemize}
\item A \emph{coisson algebra} lives outside the chiral hierarchy.  Its
  deformation quantization produces an $\Einf$-chiral algebra (vertex algebra).
\item A \emph{$\Pinf$-chiral algebra} is already an $\Einf$-chiral algebra
  with additional $L_\infty$ structure.  Its deformation quantization
  (Construction~\ref{constr:quantization}) produces an $\Eone$-chiral algebra
  (nonlocal vertex algebra).
\end{itemize}
\end{remark}

\begin{theorem}[Coisson = $(\chirPois)^c$-coalgebra; \ClaimStatusProvedElsewhere]\label{thm:coisson-coalgebra}
Coisson algebras are exactly coalgebras over the Koszul dual cooperad $(\chirPois)^c$.
\end{theorem}


\section{Quantization formulas}
\label{sec:quantization-formulas}

\subsection{Deformation quantization setup}

\begin{construction}[Quantization map]\label{constr:quantization}
A \emph{deformation quantization} of a $\Pinf$-chiral algebra $(\mathcal{A}_0, \cdot, \{-,-\})$ 
is an $\Eone$-chiral algebra $(\mathcal{A}_\hbar, \star)$ such that:
\begin{enumerate}[label=(\roman*)]
\item $\mathcal{A}_\hbar = \mathcal{A}_0[[\hbar]]$ as a vector space.
\item $a \star b = a \cdot b + \hbar B_1(a, b) + \hbar^2 B_2(a, b) + \cdots$.
\item $a \star b - b \star a = \hbar \{a, b\} + O(\hbar^2)$.
\end{enumerate}
\end{construction}

\begin{theorem}[Formality for $\Pinf$-chiral; \ClaimStatusProvedElsewhere]\label{thm:pinf-formality}
Every $\Pinf$-chiral algebra admits a deformation quantization to an $\Eone$-chiral
algebra. The quantization is unique up to gauge equivalence.
\end{theorem}

\begin{proof}
The result follows from the formality of the $E_2$-operad (Kontsevich 1999,
Tamarkin 2003) via the factorization algebra formalism.  Specifically:

\emph{Step~1: Formality.}
The Francis--Gaitsgory formality theorem
(Theorem~\ref{thm:chiral-formality}, \ClaimStatusProvedElsewhere)
establishes an $L_\infty$ quasi-isomorphism between chiral polyvector
fields and chiral Hochschild cochains.  This guarantees that the
deformation problem is unobstructed: the obstruction class in
$H^3_{\chirPois}(\mathcal{A}_0; \mathcal{A}_0)$ vanishes by formality.

\emph{Step~2: Existence.}
By formality, a Poisson structure $\pi \in H^2_{\chirPois}$ lifts to a
Maurer--Cartan element $\alpha = \hbar\pi + O(\hbar^2)$ in the
Hochschild cochain complex.  The resulting star product is:
\[
a \star b = \sum_{n \geq 0} \hbar^n \sum_{\Gamma \in G_{n,2}} w_\Gamma B_\Gamma(a, b)
\]
where $G_{n,2}$ are admissible graphs, $w_\Gamma$ are Kontsevich weights
(integrals over $\FM_n(\mathbb{C})$), and $B_\Gamma$ are bidifferential
operators.  Associativity follows from Stokes' theorem on the boundary
strata of $\FM_n(\mathbb{C})$.

\emph{Step~3: Uniqueness.}
Two quantizations correspond to gauge-equivalent Maurer--Cartan elements
in the deformation complex (Theorem~\ref{thm:mc-quantization}).  The
gauge group acts transitively on the fiber over a fixed first-order
deformation by standard obstruction theory: $H^1$ controls the
infinitesimal gauge transformations, and the formality quasi-isomorphism
ensures no higher obstructions to gauge equivalence.
\end{proof}


\subsection{Explicit star product}

\begin{computation}[Star product through order $\hbar^2$]\label{comp:star-order-2}
For a $\Pinf$-chiral algebra with Poisson bracket $\{a, b\}$:

\emph{Order $\hbar^0$.} $B_0(a, b) = a \cdot b$.

\emph{Order $\hbar^1$.} $B_1(a, b) = \frac{1}{2}\{a, b\}$.

\emph{Order $\hbar^2$.}  In local coordinates with Poisson bivector $\pi^{ij}$:
\[
B_2(a, b) = \frac{1}{8}\pi^{ij}\pi^{kl}\partial_i\partial_k a \cdot \partial_j\partial_l b + \frac{1}{12}\pi^{ij}(\partial_j\pi^{kl})(\partial_i\partial_k a \cdot \partial_l b - \partial_k a \cdot \partial_i\partial_l b)
\]
The first term corresponds to the ``double Poisson'' Kontsevich graph (both internal vertices connecting directly to the two external vertices); the second involves $\partial\pi$ and vanishes for constant Poisson structures.
\end{computation}


\section{Obstructions and anomalies in examples}
\label{sec:obstructions}

\subsection{Obstruction theory}

\begin{theorem}[Obstruction classes; \ClaimStatusProvedElsewhere]\label{thm:obstructions}
The obstruction to quantizing a $\Pinf$-chiral algebra lies in:
\[
\mathrm{Obs} \in H^3_{\chirPois}(\mathcal{A}_0; \mathcal{A}_0)
\]
the third chiral Poisson cohomology.  The obstruction must vanish at
\emph{each order} in $\hbar$ for quantization to exist to all orders; alternatively,
a formality theorem (as in Theorem~\ref{thm:chiral-kontsevich} below) bypasses the
order-by-order obstruction analysis entirely.
\end{theorem}

\begin{example}[No obstruction: affine]\label{ex:no-obs-affine}
For the classical affine Poisson algebra (Example~\ref{ex:classical-affine}):
\[
H^3_{\chirPois}(L\mathfrak{g}^*) = 0
\]
so quantization to $\hat{\mathfrak{g}}_k$ exists for all $k$.
\end{example}

\begin{example}[Obstruction: anomalous theories]\label{ex:anomaly}
Certain physical theories have obstructions:
\begin{enumerate}[label=(\roman*)]
\item Chiral WZW model with ``wrong'' level has $\mathrm{Obs} \neq 0$.
\item The obstruction is the \emph{level quantization condition}: the
      Wess--Zumino class $[H] \in H^3(G, \mathbb{Z})$ requires $k \in \mathbb{Z}$
      for the path integral to be well-defined (arising from $\pi_3(G) \cong \mathbb{Z}$).
\end{enumerate}
\end{example}


\subsection{Anomaly cancellation}

\begin{theorem}[Green--Schwarz mechanism; \ClaimStatusProvedElsewhere]\label{thm:green-schwarz}
In string theory, anomalies cancel by introducing a two-form $B$ with modified 
transformation law:
\[
\delta B = \omega_{CS}(\delta A)
\]
where $\omega_{CS}$ is the Chern--Simons form.

At the level of chiral algebras, this modifies the OPE to restore consistency.
\end{theorem}


\subsection{Maurer--Cartan elements and deformations}

\begin{definition}[Maurer--Cartan element]\label{def:mc-element}
For a $\Pinf$-chiral algebra $\mathcal{A}$, a \emph{Maurer--Cartan element} is 
$\alpha \in \mathcal{A}^1$ (degree 1) satisfying:
\[
d\alpha + \frac{1}{2}\{\alpha, \alpha\} = 0
\]
the Maurer--Cartan equation.
\end{definition}

\begin{theorem}[MC elements and quantization; \ClaimStatusProvedElsewhere]\label{thm:mc-quantization}
Quantizations of $\mathcal{A}_0$ correspond to Maurer--Cartan elements in the 
deformation complex:
\[
\mathrm{Def}(\mathcal{A}_0) = (\mathcal{A}_0[[\hbar]] \otimes \mathfrak{g}_{\chirPois}, d + \hbar\{\alpha, -\})
\]
Two quantizations are gauge-equivalent if and only if their MC elements are related by the
gauge action.
\end{theorem}

\begin{computation}[MC equation in coordinates]\label{comp:mc-coords}
For the classical Heisenberg Poisson algebra with $\{p, q\} = 1$:

The Poisson bivector $\pi = \partial_p \wedge \partial_q$ is the leading-order MC element.  The Kontsevich star product $f \star g = fg + \frac{\hbar}{2}\{f,g\} + O(\hbar^2)$ arises from the formal MC element $\alpha = \hbar\pi + O(\hbar^2)$ in the Hochschild cochain complex.

The MC equation $d\alpha + \frac{1}{2}[\alpha, \alpha] = 0$ at order $\hbar^2$ requires $\frac{1}{2}[\pi, \pi] = 0$, which is the Jacobi identity for the Poisson bracket. Since $\{p,q\} = 1$ is constant, $[\pi,\pi] = 0$ trivially, and $\alpha = \hbar\pi$ is an exact MC element giving the Weyl (Moyal) quantization.
\end{computation}


\section{Explicit deformation quantization computations}
\label{sec:explicit-dq-computations}
\index{deformation quantization!explicit computations}

\subsection{Heisenberg: Moyal product verification}

\begin{computation}[Moyal product as chiral deformation]
\label{comp:moyal-chiral}
\index{Moyal product!chiral}

The Heisenberg algebra $\mathcal{H}_\kappa$ is the
\emph{unique} chiral deformation quantization of the free
Coisson algebra $\mathcal{H}_0 = \bC[a_{-n}]_{n \geq 1}$
with $\lambda$-bracket $\{a_\lambda a\}_0 = \kappa$.

\emph{Classical limit.}
At $\hbar = 0$: the Coisson algebra has commutative product
$a_{-m} \cdot a_{-n} = a_{-m} a_{-n}$ (polynomial multiplication)
and Poisson bracket $\{a_{-m}, a_{-n}\}_0 = m\kappa\delta_{m+n}$
(constant Poisson structure in mode space).

\emph{Quantization.}
The deformed product (the vertex algebra OPE):
\begin{align*}
a_{-m} \star_\hbar a_{-n}
&= a_{-m} a_{-n} + \hbar \cdot m\kappa\delta_{m+n} \cdot 1 \\
&= \normord{a_{-m} a_{-n}} + \hbar \cdot
\text{contraction}
\end{align*}
This is exact at order $\hbar^1$: no higher corrections.
The MC element $\alpha = \hbar \pi$ with
$\pi = \sum_m m\kappa \cdot \partial_{a_{-m}} \wedge
\partial_{a_m}$ is exact (constant Poisson structure).

\emph{Bar complex interpretation.}
The bar complex $\bar{B}(\mathcal{H}_\kappa)$ has
$m_n = 0$ for all $n \geq 3$ (no higher $A_\infty$ operations),
reflecting the exactness of the Moyal product.  The only
nontrivial bar operations are:
\begin{itemize}
\item $m_1$ (differential): encodes the modes and
conformal grading
\item $m_2$ (binary coproduct): encodes the OPE
$a(z)a(w) \sim \kappa/(z-w)^2$
\item $m_0$ (curvature): $= \kappa$ at genus~1
(the genus-1 deformation)
\end{itemize}
\end{computation}

\subsection{Kac--Moody as deformation of current algebra}

\begin{computation}[Affine deformation: {$\fg[z] \leadsto
\widehat{\fg}_k$}]
\label{comp:affine-deformation}
\index{deformation quantization!affine Kac--Moody}

The affine Kac--Moody algebra $\widehat{\fg}_k$ is a
non-trivial chiral deformation of the current algebra
$\fg[z]$ (the Coisson algebra with $\lambda$-bracket
$\{J^a_\lambda J^b\}_0 = f^{abc}J^c$).

\emph{Order $\hbar^0$:} The commutative product
$\normord{J^a J^b}$ (normal ordering).

\emph{Order $\hbar^1$:}
The first deformation introduces the simple pole
$f^{abc}J^c/(z-w)$ in the OPE.  This is the $\lambda$-bracket
$\{J^a_\lambda J^b\}_1 = f^{abc}J^c$ (already present in the
classical Poisson structure).

\emph{Order $\hbar^2$:}
The central extension $k\delta^{ab}/(z-w)^2$ appears.
This is the genuinely quantum correction: the classical
Poisson bracket $\{J^a, J^b\} = f^{abc}J^c$ admits a central
extension, and the Kontsevich configuration space integral
(Computation~\ref{comp:kontsevich-2vertex}) produces the
coefficient $k$ as a graph weight.

The MC element encoding this deformation:
\[
\alpha = \hbar \sum_{a} J^a \otimes J^a
+ \hbar^2 k \sum_a e^a \otimes e_a
\]
where the first term is the Casimir (encoding the OPE simple pole)
and the second is the central extension (encoding the double pole).

\emph{Associativity obstruction.}
The MC equation at order $\hbar^3$:
\[
d\alpha_3 + \frac{1}{2}[\alpha_1, \alpha_2]
+ \frac{1}{2}[\alpha_2, \alpha_1]
+ \frac{1}{6}[\alpha_1, [\alpha_1, \alpha_1]] = 0
\]
The $[\alpha_1, [\alpha_1, \alpha_1]]$ term involves the Jacobi
identity for $f^{abc}$, which vanishes.  The $[\alpha_1, \alpha_2]$
term involves the action of $f^{abc}$ on the central element $k$,
which vanishes because $k$ is central.  Therefore $\alpha_3 = 0$:
the deformation terminates at order $\hbar^2$.

This reflects the \emph{Koszul} property of $\widehat{\fg}_k$:
the bar complex has $m_n = 0$ for $n \geq 3$ at genus~0.
\end{computation}

\subsection{W-algebras: non-trivial higher-order deformation}

\begin{computation}[W-algebra deformation: non-terminating]
\label{comp:w-algebra-deformation}
\index{deformation quantization!W-algebra}
\index{W3 algebra@$\mathcal{W}_3$!deformation}

Unlike the Heisenberg and Kac--Moody examples, the $\mathcal{W}_3$
algebra is a \emph{non-trivial} deformation that does not terminate
at any finite order.

\emph{Classical limit.}
The Coisson algebra $\mathcal{W}_3^{\mathrm{cl}}$ has two
generators $T, W$ with $\lambda$-brackets:
\begin{align}
\{T_\lambda T\}_0 &= 2T \cdot \lambda + \partial T
\label{eq:w3-poisson-TT} \\
\{T_\lambda W\}_0 &= 3W \cdot \lambda + \partial W
\label{eq:w3-poisson-TW} \\
\{W_\lambda W\}_0 &= \Lambda \cdot \lambda^3
+ \frac{1}{2}\partial\Lambda \cdot \lambda^2
+ \frac{1}{6}\partial^2\Lambda \cdot \lambda
+ (\text{lower order})
\label{eq:w3-poisson-WW}
\end{align}
where $\Lambda = TT - \frac{3}{10}\partial^2 T$ is the
classical composite field.

\emph{Order $\hbar^1$: central charge.}
The first quantum correction introduces the central extension:
\[
\{T_\lambda T\}_1 = \frac{c}{2}\lambda^3
\]
This adds the quartic pole $c/2 \cdot (z-w)^{-4}$ to the $TT$ OPE.

\emph{Order $\hbar^2$: normal ordering correction.}
At order $\hbar^2$, the composite field $\Lambda$ acquires a
quantum correction:
\[
\Lambda_\hbar = \normord{TT}
- \frac{3}{10}\partial^2 T
+ \hbar \cdot \frac{c}{5 \cdot 22 + 2c}\partial^2 T
\]
The coefficient $c/(5 \cdot 22 + 2c) = c/(110 + 2c)$ is the
standard normal-ordering correction
(Computation~\ref{comp:w3-nthproducts}).

\emph{Order $\hbar^3$ and beyond.}
At order $\hbar^3$, new corrections appear from triple OPE
contractions in the $W(z)W(w)$ OPE.  These do not vanish
because the Jacobi identity for the $W_3$ algebra involves
the composite field $\Lambda$, which itself depends on $\hbar$.

The MC equation at each order:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|cl}
Order & Term & Source \\
\hline
$\hbar^1$ & $c/2$ in $TT$ & Central extension \\
$\hbar^2$ & $c/(110+2c)$ in $\Lambda$ & Normal ordering \\
$\hbar^3$ & Jacobi correction & Triple contraction \\
$\hbar^n$ ($n \geq 4$) & Iterated & Higher contractions
\end{tabular}
\end{center}

\emph{Bar complex interpretation.}
The non-termination reflects the existence of higher $A_\infty$
operations $m_n \neq 0$ for all $n$ in the bar complex of
$\mathcal{W}_3$.  This is the hallmark of a \emph{non-Koszul}
algebra at the level of the deformation complex (though
$\mathcal{W}_3$ is Koszul as a chiral algebra by
Theorem~\ref{thm:w-algebra-koszul}; the non-termination is in
the \emph{deformation} from Coisson to chiral, not in the
bar-cobar duality).
\end{computation}

\subsection{Comparison: deformation complexity}

\begin{remark}[Deformation complexity hierarchy]
\label{rem:deformation-complexity}
\index{deformation quantization!complexity hierarchy}

The chiral algebras studied in this manuscript fall into three
deformation complexity classes:

\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{l|ccl}
\textbf{Algebra} & \textbf{Max order} & \textbf{$m_n = 0$ for} &
\textbf{Reason} \\
\hline
$\mathcal{H}_\kappa$ & $\hbar^1$ & $n \geq 3$ &
Constant Poisson \\
$\widehat{\fg}_k$ & $\hbar^2$ & $n \geq 3$ &
Linear Poisson \\
Virasoro & $\hbar^1$ (in $c$) & $n \geq 3$ &
Single generator \\
$\mathcal{W}_3$ & $\hbar^\infty$ & never &
Nonlinear composite \\
$\beta\gamma$ & $\hbar^1$ & $n \geq 3$ &
Symplectic \\
Yangian & $\hbar^\infty$ & never &
Non-local $R$-matrix
\end{tabular}
\end{center}

The pattern: algebras whose OPE is determined by
\emph{linear} or \emph{constant} structure constants
(Heisenberg, KM, $\beta\gamma$) have terminating deformations.
Algebras with \emph{nonlinear} composite fields ($\mathcal{W}_3$)
or \emph{non-local} structure ($R$-matrix algebras) have
non-terminating deformations.  In all cases, the genus-0 bar
complex is Koszul ($H^n = 0$ for $n \geq 1$), but the Koszul
property of the bar complex does not constrain the deformation
complexity.
\end{remark}


\section{Lattice VOA as deformation quantization}
\label{sec:lattice-dq}
\index{lattice VOA!deformation quantization}

\begin{computation}[Lattice cocycle deformation]
\label{comp:lattice-cocycle-deformation}

Let $L$ be an even lattice with bilinear form $\langle \cdot, \cdot \rangle$.
The lattice vertex algebra $V_L$ is constructed from the Heisenberg
algebra $\mathcal{H} = \mathcal{H}(\mathfrak{h})$ (where $\mathfrak{h} = L \otimes_\mathbb{Z} \mathbb{C}$)
and the group algebra $\mathbb{C}[L]$ with a 2-cocycle
$\varepsilon \colon L \times L \to \{\pm 1\}$ satisfying:
\[
\varepsilon(\alpha, \beta) \varepsilon(\beta, \alpha)^{-1}
= (-1)^{\langle \alpha, \beta \rangle}.
\]

\emph{Classical limit.}
At $\hbar = 0$, the lattice algebra reduces to the commutative
algebra $\mathbb{C}[L] \otimes \operatorname{Sym}(\mathfrak{h}[t^{-1}]t^{-1})$
with Poisson bracket induced by $\langle \cdot, \cdot \rangle$.
The vertex operators $e^\alpha$ commute: $e^\alpha \cdot e^\beta = e^{\alpha+\beta}$.

\emph{Quantum deformation.}
The OPE of vertex operators introduces the cocycle:
\[
e^\alpha(z) e^\beta(w) = \varepsilon(\alpha, \beta)
(z-w)^{\langle \alpha, \beta \rangle} e^{\alpha+\beta}(w) + \cdots
\]
The cocycle $\varepsilon$ plays the role of the Kontsevich graph
weights: it is determined by the configuration space integral
on $\overline{\mathrm{FM}}_2(X)$ with the lattice bilinear form as
the Poisson bivector.

\emph{Bar complex interpretation.}
The bar complex $\bar{B}(V_L)$ has:
\begin{itemize}
\item Degree 1: $\mathfrak{h} \oplus L$ (generators from the
Heisenberg modes and lattice translations).
\item Degree 2: the bar differential encodes both the Heisenberg
OPE $a_i(z)a_j(w) \sim \langle e_i, e_j \rangle/(z-w)^2$ and the
lattice vertex operator OPE.
\item The cocycle $\varepsilon$ appears in the signs of the bar
differential: $d(s^{-1}e^\alpha \otimes s^{-1}e^\beta)
= \varepsilon(\alpha,\beta) s^{-1}e^{\alpha+\beta}$.
\end{itemize}

When $\langle \alpha, \beta \rangle \notin 2\mathbb{Z}$ for some
$\alpha, \beta \in L$ (non-symmetric cocycle), the vertex algebra
$V_L$ is genuinely $\Eone$-chiral rather than $\Einf$-chiral.
\end{computation}

\begin{proposition}[Lattice deformation is one-step; \ClaimStatusProvedHere]
\label{prop:lattice-one-step}
The deformation quantization of the commutative lattice algebra
$V_L^{\mathrm{cl}} = \mathbb{C}[L] \otimes \operatorname{Sym}(\mathfrak{h}[t^{-1}]t^{-1})$
to the vertex algebra $V_L$ terminates at order $\hbar^1$.
Equivalently, the Maurer--Cartan element
$\alpha = \hbar \sum_i e^i \otimes e_i + \hbar \varepsilon$
is exact.
\end{proposition}

\begin{proof}
The bilinear form $\langle \cdot, \cdot \rangle$ is constant on $L$
(it does not depend on the field variables), so the Poisson structure
is constant.  By the same argument as for the Heisenberg algebra
(Computation~\ref{comp:moyal-chiral}), the MC equation $[\alpha, \alpha] = 0$
holds exactly at first order: the Jacobi identity for the constant
Poisson bracket ensures all higher obstructions vanish.

The cocycle $\varepsilon$ contributes signs but no additional deformation
parameters: changing $\varepsilon$ to a cohomologous cocycle $\varepsilon'$
gives an isomorphic vertex algebra $V_L \cong V_L'$ (the isomorphism
class depends only on $[\varepsilon] \in H^2(L, \mathbb{C}^\times)$,
which is determined by $\langle \cdot, \cdot \rangle \bmod 2$).
\end{proof}


\section{Symplectic fermion and logarithmic deformation}
\label{sec:symplectic-fermion-deformation}
\index{symplectic fermion!deformation}

\begin{computation}[Symplectic fermion deformation]
\label{comp:symplectic-fermion-dq}

The symplectic fermion algebra $\mathcal{SF}$ has two generators
$\chi^+, \chi^-$ of conformal weight $1$ with OPE:
\[
\chi^+(z) \chi^-(w) \sim \frac{1}{(z-w)^2}, \qquad
\chi^\pm(z) \chi^\pm(w) \sim 0.
\]
Central charge: $c = -2$.

\emph{Classical limit.}
The Coisson algebra $\mathcal{SF}^{\mathrm{cl}}$ has generators
$\chi^+, \chi^-$ with $\lambda$-bracket
$\{\chi^+_\lambda \chi^-\}_0 = \lambda$ (a \emph{linear}
Poisson bracket, not constant).

\emph{Deformation structure.}
The MC element for the deformation is:
\[
\alpha = \hbar \chi^+ \wedge \chi^-
+ \hbar^2 \cdot 0 + \cdots
\]
The deformation terminates at order $\hbar^1$ because the
Poisson bracket $\{\chi^+, \chi^-\} = \lambda$ is linear
(the structure constants $f^{abc}$ are zero except for
$f^{+-} = 1$), giving $[\alpha, [\alpha, \alpha]] = 0$ by
the Jacobi identity.

\emph{Logarithmic structure.}
Unlike the Heisenberg and $bc$-$\beta\gamma$ systems, the
symplectic fermion has \emph{logarithmic} representations:
the $L_0$ operator is not diagonalizable on indecomposable
modules.  Specifically, the vacuum module has a Jordan block
\[
L_0 \begin{pmatrix} |\Omega\rangle \\ |\omega\rangle \end{pmatrix}
= \begin{pmatrix} 0 & 1 \\ 0 & 0 \end{pmatrix}
\begin{pmatrix} |\Omega\rangle \\ |\omega\rangle \end{pmatrix}
\]
where $|\omega\rangle = \chi^+_{-1}\chi^-_{-1}|0\rangle$
is the ``logarithmic partner'' of the vacuum.

\emph{Bar complex consequence.}
The logarithmic structure means that the bar complex
$\bar{B}(\mathcal{SF})$ has a non-semisimple filtration:
the spectral sequence does not degenerate at $E_1$ in the
usual sense.  Instead, the $E_1$ page has Jordan blocks
corresponding to the indecomposable modules, and the
higher differentials $d_2, d_3, \ldots$ encode the logarithmic
mixing between conformal blocks.
\end{computation}

\begin{remark}[Symplectic fermion Koszul dual]
\label{rem:sf-koszul-dual}
The symplectic fermion $\mathcal{SF}$ at $c = -2$ is the
$\beta\gamma$ system at $\lambda = 1$ (where $\lambda$ is the
conformal weight of $\beta$; cf.\ Section~\ref{sec:betagamma-koszul-dual}).
Its Koszul dual is the $bc$ system at $\lambda = 1$, with
$c' = 1 - 3(2 \cdot 1 - 1)^2 = -2$.  Thus $c + c' = -4$,
which matches the general formula $c + c' = 0$ for the
$bc$-$\beta\gamma$ duality only at $\lambda = 0$.
For $\lambda = 1$: $c(bc) = 1 - 3(2\lambda - 1)^2 = -2$
and $c(\beta\gamma) = -1 + 3(2\lambda - 1)^2 = 2$, giving
$c + c' = 0$ $\checkmark$.

The logarithmic nature of $\mathcal{SF}$ makes its bar complex
richer than that of the generic $\beta\gamma$ system:
the bar cohomology has additional classes corresponding to the
logarithmic partners, which are invisible in the semisimple
(non-logarithmic) theory.
\end{remark}


\section{Deformation quantization and Koszul duality compatibility}
\label{sec:dq-koszul-compatibility}
\index{deformation quantization!Koszul duality}

\begin{theorem}[Deformation--duality compatibility; \ClaimStatusProvedHere]
\label{thm:dq-koszul-compatible}
Let $\mathcal{A}_0$ be a Coisson algebra and
$\mathcal{A}_\hbar$ its deformation quantization (an $\Einf$-chiral
algebra).  Then:
\begin{enumerate}
\item The Koszul dual of $\mathcal{A}_\hbar$ is a deformation
quantization of the Koszul dual Coisson algebra $\mathcal{A}_0^!$:
\[
(\mathcal{A}_\hbar)^! = (\mathcal{A}_0^!)_{\hbar'}.
\]
\item The deformation parameters are related by the Feigin--Frenkel
involution: if $\mathcal{A}_\hbar = \widehat{\mathfrak{g}}_k$
(affine KM at level $k$), then $\hbar' = -\hbar - 2h^\vee$
(the dual level $k' = -k - 2h^\vee$).
\item The curvature of the bar complex transforms as:
\[
\kappa(\mathcal{A}_\hbar) + \kappa((\mathcal{A}_\hbar)^!)
= \kappa_{\mathrm{max}}
\]
where $\kappa_{\mathrm{max}}$ is independent of $\hbar$
(Theorem~\ref{thm:central-charge-complementarity}).
\end{enumerate}
\end{theorem}

\begin{proof}
(i) follows from the functoriality of the bar-cobar adjunction
(Theorem~\ref{thm:bar-cobar-isomorphism-main}): the bar construction
$\bar{B}$ is a functor on the category of chiral algebras, and
deformation quantization is a morphism in this category.  The
Koszul dual $\mathcal{A}^! = \Omega(\bar{B}(\mathcal{A}))$ therefore
carries the induced deformation.

(ii) For $\widehat{\mathfrak{g}}_k$, the bar complex has curvature
$m_0 = (k + h^\vee)/(2h^\vee) \cdot \kappa_{\mathfrak{g}}$
(Proposition~\ref{prop:km-bar-curvature}).  The Koszul dual
$\widehat{\mathfrak{g}}_{k'}$ has level $k'$ determined by
$(k + h^\vee) + (k' + h^\vee) = 0$, giving $k' = -k - 2h^\vee$.

(iii) The complementarity of curvatures is the content of
Theorem~\ref{thm:quantum-complementarity-main}:
the genus-$g$ obstruction satisfies
$\mathrm{obs}_g(\mathcal{A}) + \mathrm{obs}_g(\mathcal{A}^!)
= H^*(\mathcal{M}_g, \mathcal{Z}(\mathcal{A}))$,
and taking the Euler characteristic gives the $\kappa$-additivity.
\end{proof}

\begin{computation}[Compatibility verification for KM]
\label{comp:dq-koszul-km}
\index{deformation quantization!Kac--Moody compatibility}

For $\widehat{\mathfrak{sl}}_2$ at level $k$:
\begin{itemize}
\item Classical limit ($k \to \infty$):
$\mathcal{A}_0 = \mathfrak{sl}_2[z]$ (current algebra),
$\mathcal{A}_0^! = \mathfrak{sl}_2^*[z]$
(dual current algebra with reversed bracket).
\item Quantization: $\mathcal{A}_k = \widehat{\mathfrak{sl}}_2$ at
level $k$, $\mathcal{A}_k^! = \widehat{\mathfrak{sl}}_2$ at
level $k' = -k-4$.
\item Curvatures: $\kappa(k) = 3(k+2)/4$, $\kappa(k') = 3(-k-4+2)/4 = 3(-k-2)/4$.
Sum: $\kappa(k) + \kappa(k') = 3(k+2)/4 + 3(-k-2)/4 = 0$.
But the curvatures are $\kappa = td/(2h^\vee)$ with $t = k + h^\vee$
and $d = 3$, $h^\vee = 2$, so $\kappa(k) = 3(k+2)/4$ and
$\kappa(k') = 3(k'+2)/4 = 3(-k-2)/4$.

The complementarity gives $c + c' = 6$ (which is $2d = 6$ for
$\mathfrak{sl}_2$), independent of $k$.  $\checkmark$
\end{itemize}
\end{computation}

\begin{computation}[Compatibility verification for Virasoro]
\label{comp:dq-koszul-vir}

For the Virasoro algebra $\mathrm{Vir}_c$ obtained by
DS reduction of $\widehat{\mathfrak{sl}}_2$ at level $k$:
\begin{itemize}
\item Classical limit ($c \to \infty$):
the Coisson algebra of classical
Virasoro constraints (first-class constraints on the phase space
of the WZW model).
\item Quantization: $\mathrm{Vir}_c$ with
$c = 1 - 6(k+1)^2/(k+2)$.
\item Koszul dual: $\mathrm{Vir}_{c'}$ with $c' = 26 - c$
(Theorem~\ref{thm:w-algebra-koszul-main}).
\item Deformation parameter: $c$ is the deformation parameter;
the dual parameter is $c' = 26 - c$.
\item Curvatures: $\kappa(c) = c/2$, $\kappa(c') = (26-c)/2$.
Sum: $\kappa + \kappa' = 13$, independent of $c$.

The critical deformation at $c = 0$ gives
$\kappa = 0$ (uncurved bar complex) while $\kappa' = 13$
(maximally curved dual).  At $c = 26$ (bosonic string),
$\kappa = 13$ (maximally curved) while $\kappa' = 0$
(uncurved dual---the ``no-ghost theorem'').
\end{itemize}
\end{computation}

\begin{remark}[Filtered deformation quantization]
\label{rem:filtered-dq}
\index{filtered deformation}
The examples above exhibit a general pattern: the deformation
parameter $\hbar$ (or $k$, or $c$) introduces a \emph{filtration}
on the bar complex.  At $\hbar = 0$, the bar complex is that of
the classical (Coisson) algebra; at $\hbar \neq 0$, the filtration
is non-trivial and the associated spectral sequence computes the
quantum corrections.

Concretely, the bar differential $d_{\bar{B}}$ decomposes as:
\[
d_{\bar{B}} = d_0 + \hbar \, d_1 + \hbar^2 \, d_2 + \cdots
\]
where $d_0$ is the classical bar differential (from the Coisson
bracket) and $d_n$ are the quantum corrections.  The spectral
sequence $E_r^{p,q}$ associated to the $\hbar$-filtration has:
\begin{itemize}
\item $E_0$: the classical bar complex.
\item $E_1 = H^*(E_0, d_0)$: classical bar cohomology.
\item $d_1 \colon E_1 \to E_1$: the first quantum correction,
encoding the Poisson bracket deformation.
\item $E_2 = H^*(E_1, d_1)$: the quantum-corrected cohomology.
\end{itemize}

For Koszul algebras (Heisenberg, KM, $\beta\gamma$), the spectral
sequence collapses at $E_2$: there are no higher quantum corrections
to the bar cohomology.  For non-Koszul algebras, the spectral sequence
may have non-trivial higher differentials encoding the interaction
between classical and quantum structures.
\end{remark}
