\chapter{Exceptional-type Yangian Koszul duality: the RTT obstruction}
\label{chap:exceptional-yangian-koszul-duality-platonic}

\providecommand{\ClaimStatusProvedHere}{\textsc{ProvedHere}}
\providecommand{\ClaimStatusProvedElsewhere}{\textsc{ProvedElsewhere}}
\providecommand{\ClaimStatusConjectured}{\textsc{Conjectured}}
\providecommand{\ClaimStatusHeuristic}{\textsc{Heuristic}}
\providecommand{\PhiFA}{\Phi^{\mathrm{FA}}}
\providecommand{\SpCh}{\mathrm{Sp}^{\mathrm{ch}}}

\begin{remark}[Archetype tagging and Vol~III shadow for the Yangian
families]
\label{rem:exceptional-yangian-archetype-and-volIII-shadow}
\index{Yangian!archetype tagging}
\index{five-archetype dichotomy!Yangian taxa}
\index{five-invariant distinction!exceptional Yangian RTT chapter}
\index{two-stage CY-to-chiral distinction!K3 Hall--Drinfeld two-stage shadow}
Type signature: (Open quadrant for the affine chiral side of the
classical Yangian--chiral correspondence; CY quadrant for the K3
Hall--Drinfeld target via the Vol~III two-stage factorisation
$\Phi_d^{(\Sigma_{d-1},C)}=\SpCh_{\Sigma_{d-1},C}\circ\PhiFA_d$;
chart-level presentation for the Yangian taxa as filtered Hopf
algebras over $\C[[\hbar]]$ \textup{(}taxa
\textup{(D)},\textup{(R)},\textup{(E)},\textup{(K)} of
Proposition~\ref{prop:exceptional-yangian-type-separation}\textup{)};
the affine companion taxon \textup{(A)} occupies the chart level
of the standard Open-quadrant Beilinson tower as the chiral
algebra $V_k(\fg)$).

The Yangians \textup{(D)},\textup{(R)},\textup{(E)} of
Proposition~\ref{prop:exceptional-yangian-type-separation} are
not themselves chiral algebras on a curve and therefore do not
carry chart-level five-stratum rows of their own. Their chiral
companion is the affine taxon \textup{(A)},
$V_k(\fg)$, a class~$\mathbf L$ chart algebra
\textup{(}Theorem~\ref{thm:archetype-shadow-classification},
landscape census line~\ref{tab:five-by-five-kappa-stratification}
row $\mathbf L$\textup{)} whose $5\times5$ $\kappa$-stratification
row is
\[
\bigl(\kappa_{\mathrm{cat}},\kappa^{\mathrm{Hodge}}_{\mathrm{ch}},
\kappa^{\mathrm{Heis}}_{\mathrm{ch}},\kappa_{\mathrm{BKM}},
\kappa_{\mathrm{fiber}}\bigr)\bigl(V_k(\fg)\bigr)
=\bigl(0,\,0,\,\dim(\fg)(k+h^\vee)/(2h^\vee),\,-,\,
\operatorname{rank}\fg\bigr),
\]
specialising on the exceptional series to the
$\dim\fg$, $h^\vee$, $\operatorname{rank}$ data of
Corollary~\ref{cor:exceptional-yangian-graded}. The five entries
are five distinct invariants on five distinct lanes
\textup{(}five-invariant distinction\textup{)}: the
Heisenberg-slot chiral central charge
$\dim(\fg)(k+h^\vee)/(2h^\vee)$ is not the categorical scalar
$\kappa_{\mathrm{cat}}=\chi(\cO)$ of any CY host attached to
$V_k(\fg)$ (none is asserted here), and neither is the fibre rank
$\operatorname{rank}\fg$.

The K3 Hall--Drinfeld taxon \textup{(K)} of
Proposition~\ref{prop:exceptional-yangian-type-separation},
\[
\mathbf H_{\Delta_5}
=\mathcal D_\hbar\bigl(\mathcal Y^{\mathrm{Hall}}_\hbar
(\mathrm{CoHA}_{K3\times E})\bigr),
\]
sits in the class~$\mathbf B$ row anchored at K3$\times E$ with
five-stratum coordinates
$(\kappa_{\mathrm{cat}},\kappa^{\mathrm{Hodge}}_{\mathrm{ch}},
\kappa^{\mathrm{Heis}}_{\mathrm{ch}},\kappa_{\mathrm{BKM}},
\kappa_{\mathrm{fiber}})=(0,0,3,5,24)$ via the Vol~III two-stage
factorisation
\[
\PhiFA_3\bigl(D^b\Coh(K3\times E)\bigr)
\xrightarrow{\;\SpCh_{\Sigma_2,C}\;}\mathbf H_{\Delta_5},
\qquad
\Phi_3^{(\Sigma_2,C)}=\SpCh_{\Sigma_2,C}\circ\PhiFA_3,
\]
with $(\Sigma_2,C)$ the named transverse two-real-dimensional
manifold and reference curve of
landscape\_census.tex
Table~\ref{tab:five-by-five-kappa-stratification} \textup{(}Master
Two-stage CY-to-chiral distinction: the two-stage decomposition is named, never a
one-stage $\Phi_d$\textup{)}. The K3 row constants
$\kappa_{\mathrm{BKM}}(\Delta_5)=c_{\Delta_5}(0)/2=5$
\textup{(}Gritsenko 1999, paramodular weight-$5$ Borcherds product
input; the universal Borcherds-weight identity
$\kappa_{\mathrm{BKM}}(\Phi_N)=c_N(0)/2$ with $N\in\{1,2,3,4,6\}$
is a different scope, indexing CHL towers and giving values
$5,4,3,2,1$\textup{)},
$K^{\kappa_{\mathrm{ch}}}=8$,
$\kappa^{\mathrm{Heis}}_{\mathrm{ch}}(K3\times E)=3$,
$\kappa_{\mathrm{cat}}(K3\times E)=0$,
$\kappa_{\mathrm{fiber}}(K3)=24$
live on five distinct lanes; the value
$\kappa_{\mathrm{BKM}}=5$ is not the same number as
$K^{\kappa_{\mathrm{ch}}}=8$ nor as
$\kappa_{\mathrm{fiber}}(K3)=24$. None of these K3 constants is a
Drinfeld-Yangian RTT input for an exceptional finite-dimensional
$\fg$; transferring them to the exceptional RTT lane requires the
explicit comparison maps named in
Proposition~\ref{prop:exceptional-yangian-no-dk-root-k3-promotion}.
\end{remark}

\section{Finite RTT windows}
\label{sec:exceptional-yangian-finite-rtt-windows}

The Yangian Koszul-duality statement in
Theorem~\ref{thm:yangian-koszul-dual} is a theorem about a completed
RTT tower.  It is not a theorem about an abstract Drinfeld
second-presentation algebra until the Drinfeld generators have been
identified with a quadratic RTT/FRT presentation on the same filtered
object.  The proof has four independent inputs:
\begin{enumerate}[label=(\roman*)]
\item a finite-dimensional quadratic RTT window
$A_{\leq N}^{\mathrm{RTT}}=T(V_{\leq N})/\langle R_{\leq N}\rangle$
coming from an actual Yangian module packet, not only from the
underlying $\fg$-module;
\item a PBW theorem compatible with the RTT filtration, so that the
quadratic Rees special fibre is the Koszul algebra $\mathrm{Sym}(V_{\leq N})$;
\item the finite matrix identity
$R_{\leq N}^{\perp}=\operatorname{im}\Phi_{R_\hbar^{-1}}$ under the
trace pairing on $V_{\leq N}^{*}\otimes V_{\leq N}^{*}$;
\item scalar-gauge equivalence between the inverse kernel
$R_\hbar^{-1}$ and the sign-reversed kernel $R_{-\hbar}$ in the
completed spectral Laurent ring.
\end{enumerate}
Only after these four assertions are known in the same presentation does
one obtain
\[
Y_\hbar(\fg)^{!,\mathrm{ch}}
\cong
Y_{R^{-1}}(\fg)^{\mathrm{ch}}
\cong
Y_{-\hbar}(\fg)^{\mathrm{ch}}.
\]
Here $A^!$ denotes the quadratic Koszul dual algebra.  It is not the bar
coalgebra $B(A)$, and it is not the derived Hochschild centre
$Z_{\mathrm{ch}}^{\mathrm{der}}(A)$.

\section{Yangian taxa and comparison maps}
\label{sec:exceptional-yangian-taxa}

\begin{proposition}[Type separation for Yangian-facing claims;
\ClaimStatusProvedHere]
\label{prop:exceptional-yangian-type-separation}
\index{Yangian!taxonomy}
\index{K3!Hall--Drinfeld double versus Drinfeld Yangian}
The five objects below occupy different ambient categories, and no
statement about one of them transfers to another without a named
comparison functor preserving the relevant filtration, relation space,
and completion.
\begin{description}[itemsep=3pt, leftmargin=2.0em, style=nextline]
\item[\textup{(D)} Drinfeld Yangian.]
$Y_\hbar(\fg)$ is the Drinfeld Yangian of a finite-dimensional simple
Lie algebra $\fg$, given in Drinfeld's new realisation or an equivalent
$J$-presentation.
\item[\textup{(R)} RTT/FRT Yangian window.]
$A^{\mathrm{RTT}}_\hbar(\fg,V_0)$ is a quadratic algebra built from an
$R$-matrix acting on a fixed finite-dimensional $\fg$-module~$V_0$.
An isomorphism from \textup{(D)} to \textup{(R)} is an extra
presentation theorem.
\item[\textup{(A)} Affine Kac--Moody chiral algebra.]
$V_k(\fg)$, or $\widehat{\fg}_k$, is a vertex/chiral algebra at affine
level~$k$.  Its Feigin--Frenkel level reflection
$k\mapsto -k-2h^\vee$ belongs to the affine family and is not the
Yangian sign change $\hbar\mapsto-\hbar$.
\item[\textup{(E)} Affine, toroidal, and elliptic Yangian lineages.]
Affine Yangians, quantum toroidal algebras, and elliptic Yangian
objects use different base parameters and completions.  They do not
supply an RTT presentation of $Y_\hbar(E_6)$, $Y_\hbar(E_7)$,
$Y_\hbar(E_8)$, $Y_\hbar(F_4)$, or $Y_\hbar(G_2)$.
\item[\textup{(K)} K3 Hall--Drinfeld/BKM target.]
The K3 chiral bialgebra target is the Hall--Drinfeld double
\[
\mathbf H_{\Delta_5}
=
\mathcal D_\hbar\bigl(
\mathcal Y^{\mathrm{Hall}}_\hbar(\mathrm{CoHA}_{K3\times E})
\bigr),
\]
with BKM denominator data attached to $\Delta_5$.  It is not a
Drinfeld Yangian $Y_\hbar(\fg)$ for finite-dimensional~$\fg$, and the
Borcherds--Kac--Moody algebra $\mathfrak g_{\Delta_5}$ is a
vertex-operator completion object, not a finite-type Yangian input.
\end{description}
Consequently, an RTT, QYBE, CYBE, $r$-matrix, Drinfeld--Kohno,
quantum-group, Hall, or BKM assertion proves a bar-cobar, Koszul,
Verdier, or chiral-Hochschild assertion only after the corresponding
comparison map to the ordered $E_1$ bar complex and its continuous dual
has been supplied.
\end{proposition}

\begin{proof}
The separations \textup{(D)}--\textup{(E)} are the taxonomy recorded in
the Yangian foundations chapter, and \textup{(K)} is the K3 separation
in the concordance.  The functors and completions differ: Drinfeld
generators live in a Hopf algebra over $\C[[\hbar]]$, RTT windows are
quadratic finite-level quotients, affine Kac--Moody algebras are
chiral algebras at level~$k$, and the K3 object is Hall/CoHA-based
with a BKM denominator.  Since the bar-cobar and Hochschild
constructions are functorial only after the source algebra, topology,
and differential have been fixed, none of the listed objects can
replace another by notation alone.
\end{proof}

\section{The RTT criterion}
\label{sec:exceptional-yangian-template}

\begin{proposition}[Finite-window inverse-kernel criterion;
\ClaimStatusProvedHere]
\label{prop:exceptional-yangian-template}
Type signature: (Open-quadrant chart-level for the affine
companion $V_k(\fg)$; chain-level RTT presentation for the
filtered Yangian Hopf algebra; Beilinson level $1\leftrightarrow 2$
quadratic Koszul duality between RTT relation space and inverse
kernel; hypothesis package: \textup{(a)}--\textup{(d)} below; the
quadratic Koszul dual $A^!$ of
Convention~\ref{conv:master-five-object-firewall} is distinct
from the bar coalgebra $B(A)$ and from the derived chiral centre
$Z^{\mathrm{der}}_{\mathrm{ch}}(A)$).

Let $\fg$ be a simple complex Lie algebra and let $V_0$ be a
finite-dimensional faithful $\fg$-module.  Suppose that
$Y_\hbar(\fg)$ admits an RTT/FRT presentation
$A^{\mathrm{RTT}}_\hbar(\fg,V_0)$ whose finite level windows
$A_{\leq N}$ satisfy the following four conditions.
\begin{enumerate}[label=\textup{(\alph*)}]
\item $A_{\leq N}=T(V_{\leq N})/\langle R_{\leq N}\rangle$ is a locally
finite quadratic algebra, with RTT relation space
$R_{\leq N}\subset V_{\leq N}\otimes V_{\leq N}$.
\item The RTT filtration is PBW and the quadratic Rees special fibre is
$\mathrm{Sym}(V_{\leq N})$.
\item Under the trace pairing, $R_{\leq N}^{\perp}$ is the relation
space of the inverse-kernel RTT algebra $A_{\leq N}(R_\hbar^{-1})$.
\item $R_\hbar^{-1}$ and $R_{-\hbar}$ differ by an invertible scalar
Laurent gauge, hence define the same RTT relation space.
\end{enumerate}
Then
\[
A_{\leq N}^{!,\mathrm{ch}}\cong A_{\leq N}(R_{-\hbar})^{\mathrm{ch}}
\]
for every finite window.  If the windows form the stabilized
Mittag--Leffler RTT tower of
Theorem~\ref{thm:shifted-rtt-stabilized-recovery}, then
\[
\widehat{A}^{!,\mathrm{ch}}_\hbar(\fg,V_0)
\cong
\widehat{A}^{\mathrm{ch}}_{-\hbar}(\fg,V_0)
\]
as completed $E_1$-chiral quadratic algebras.
\end{proposition}

\begin{proof}
The quadratic dual of $T(V_{\leq N})/\langle R_{\leq N}\rangle$ is
$T(V_{\leq N}^{*})/\langle R_{\leq N}^{\perp}\rangle$.  Hypothesis
\textup{(c)} identifies this dual relation space with the inverse-kernel
RTT relation space.  Hypothesis \textup{(d)} replaces the inverse kernel
by the sign-reversed kernel without changing relations, since central
invertible scalar factors cancel from the RTT equation.  Hypotheses
\textup{(a)} and \textup{(b)} are exactly the locally finite PBW-Koszul
input used by Polishchuk--Positselski~\cite{PP05} and by the completed
bar-cobar passage in \cite{Positselski11}.  The passage from finite
windows to the completed tower is the weightwise stabilization and
Mittag--Leffler argument already isolated in
Theorem~\ref{thm:yangian-koszul-dual} and
Theorem~\ref{thm:rtt-mittag-leffler}.
\end{proof}

\begin{remark}[Chevalley involution]
\label{rem:exceptional-chevalley-intrinsic}
The Chevalley involution of a simple Lie algebra is intrinsic at the
Cartan-root level: $e_i\mapsto -f_i$, $f_i\mapsto -e_i$,
$h_i\mapsto -h_i$.  This proves a Lie-algebra involution.  It does not
by itself prove hypothesis \textup{(d)} above.  A Yangian-level
Chevalley lift must be checked in the same RTT/FRT presentation and
must be shown to carry the chosen kernel to the inverse kernel, up to
scalar Laurent gauge.
\end{remark}

\begin{lemma}[Finite-window evidence and tower promotion;
\ClaimStatusProvedHere]
\label{lem:exceptional-finite-window-promotion}
A computation of $R_{\leq N}^{\perp}$ for one finite exceptional RTT
window proves only the $N$-th quadratic dual statement.  It promotes to
the completed exceptional Yangian only after the relation-space
identifications are compatible with the truncation maps
$A_{\leq N+1}\twoheadrightarrow A_{\leq N}$, the finite-window bar
complexes stabilize weightwise, and the resulting inverse system is
Mittag--Leffler on every finite total window.
\end{lemma}

\begin{proof}
The completed RTT object is an inverse limit of finite windows.  A
quadratic-dual calculation in one window identifies
$T(V_{\leq N}^{*})/\langle R_{\leq N}^{\perp}\rangle$ with the
inverse-kernel window at that level.  The limit statement additionally
requires that these identifications commute with the transition maps.
Without this compatibility, the inverse kernels may agree at fixed
$N$ while the completed relation space acquires a nonzero
$\varprojlim^{1}$ obstruction.  The stabilized recovery theorem
Theorem~\ref{thm:shifted-rtt-stabilized-recovery} and the
Mittag--Leffler criterion of Theorem~\ref{thm:rtt-mittag-leffler} are
exactly the hypotheses that remove this obstruction.
\end{proof}

\begin{proposition}[Ordered bar data before symmetric averaging;
\ClaimStatusProvedHere]
\label{prop:exceptional-yangian-ordered-bar-averaging}
\index{Yangian!ordered bar data}
\index{averaging map!RTT relation space}
Let $A_{\leq N}=T(V_{\leq N})/\langle R_{\leq N}\rangle$ be a finite
RTT window satisfying the quadratic local-finiteness hypotheses of
Proposition~\ref{prop:exceptional-yangian-template}.  The ordered
$E_1$ datum used by Koszul duality is
\[
\mathcal B_{\leq N}^{E_1}(A)
=
\bigl(T^c(s^{-1}\overline A_{\leq N}),\, d_{\mu},\,
\Delta_{\mathrm{dec}},\, R_{\leq N}\subset V_{\leq N}^{\otimes2}\bigr),
\]
where $d_{\mu}$ is induced by the ordered multiplication in
$A_{\leq N}$ and $\Delta_{\mathrm{dec}}$ is deconcatenation.  The
symmetric averaging map
\[
\operatorname{Av}_N:T^c(s^{-1}\overline A_{\leq N})
\longrightarrow
\bigoplus_{m\geq0}
\bigl(s^{-1}\overline A_{\leq N}\bigr)^{\otimes m}_{\Sigma_m}
\]
preserves scalar Euler data and Hilbert-series shadows when these are
defined, but it kills the ordered tensor information in
\[
x\otimes y-(-1)^{|x||y|}y\otimes x,\qquad
R_{\leq N}\subset V_{\leq N}\otimes V_{\leq N},
\]
and therefore does not determine the inverse-kernel identity
$R_{\leq N}^{\perp}=\operatorname{Rel}(A_{\leq N}(R_\hbar^{-1}))$.
\end{proposition}

\begin{proof}
The $E_1$ bar coalgebra is the tensor coalgebra on suspended
augmentation generators, with deconcatenation remembering the order of
colliding inputs.  Passing to $\Sigma_m$-coinvariants identifies
ordered words differing by graded permutation.  The relation-space
orthogonal complement is a subspace of the ordered tensor square
$V_{\leq N}^{*}\otimes V_{\leq N}^{*}$; its comparison with the
inverse-kernel RTT relation space is therefore invisible after
coinvariants unless a section or comparison map has already been
constructed.  Thus symmetric averaged data may test scalar shadows, but
it cannot prove the ordered quadratic-dual statement.
\end{proof}

\section{The cited PBW input}
\label{sec:exceptional-yangian-pbw}

\begin{proposition}[Scope of Guay--Regelskis--Wendlandt;
\ClaimStatusProvedElsewhere]
\label{thm:exceptional-yangian-pbw-grw18}
The paper cited as \cite{GRW18}, arXiv:1706.05176, is
\emph{Equivalences between three presentations of orthogonal and
symplectic Yangians}.  It proves presentation-equivalence results for
orthogonal and symplectic Yangians.  It is not a PBW theorem for
$Y_\hbar(E_6)$, $Y_\hbar(E_7)$, $Y_\hbar(E_8)$, $Y_\hbar(F_4)$, or
$Y_\hbar(G_2)$.
\end{proposition}

\begin{proof}
The title, abstract, and theorem statements of \cite{GRW18} concern
orthogonal and symplectic Yangians.  Those are the classical families
$B$, $C$, and $D$ in RTT form.  No exceptional simple Lie algebra occurs
as a target of its third-presentation theorem.  Therefore this citation
cannot supply the exceptional PBW input required by
Proposition~\ref{prop:exceptional-yangian-template}.
\end{proof}

\begin{corollary}[Exceptional current-algebra dimensions;
\ClaimStatusProvedHere]
\label{cor:exceptional-yangian-graded}
\index{Yangian!associated graded}
The root-system data used in any exceptional PBW theorem must have
\[
\begin{array}{c|ccccc}
\fg & E_6 & E_7 & E_8 & F_4 & G_2\\ \hline
\dim\fg & 78 & 133 & 248 & 52 & 14\\
h^\vee & 12 & 18 & 30 & 9 & 4
\end{array}
\]
and the affine Kac--Moody modular constants in
Chapter~\ref{ch:landscape-census} are
\[
\kappa(\widehat{E}_{6,k})=\frac{13(k+12)}4,\quad
\kappa(\widehat{E}_{7,k})=\frac{133(k+18)}{36},\quad
\kappa(\widehat{E}_{8,k})=\frac{62(k+30)}{15},
\]
\[
\kappa(\widehat{F}_{4,k})=\frac{26(k+9)}9,\qquad
\kappa(\widehat{G}_{2,k})=\frac{7(k+4)}4.
\]
The affine Feigin--Frenkel reflected levels are
\[
\begin{array}{c|ccccc}
\fg & E_6 & E_7 & E_8 & F_4 & G_2\\ \hline
k' & -k-24 & -k-36 & -k-60 & -k-18 & -k-8
\end{array}
\]
These are root-system and affine Kac--Moody data.  They do not prove a
Yangian PBW theorem.
\end{corollary}

\begin{proof}
The dimensions and dual Coxeter numbers are the exceptional rows of
the canonical affine table in
Chapter~\ref{ch:landscape-census}.  The displayed $\kappa$ values are
the specialization of
$\kappa(V_k(\fg))=\dim(\fg)(k+h^\vee)/(2h^\vee)$, and the reflected
levels are $k'=-k-2h^\vee$.  PBW for
$Y_\hbar(\fg)$ would additionally identify the associated graded of the
Yangian filtration with $U(\fg[t])$; that assertion is not a consequence
of the numerical table.
\end{proof}

\begin{proposition}[Fundamental packets are not RTT certificates;
\ClaimStatusProvedHere]
\label{prop:exceptional-fundamental-packet-scope}
\index{Yangian!exceptional fundamental packet}
The local exceptional representation data supply only low-degree
spectral checks.  They do not by themselves construct exceptional
evaluation modules or an RTT/FRT presentation of
$Y_\hbar(\fg)$.  In the local normalization the certified packet is:
\[
\begin{array}{c|c|c}
\fg & \text{lane} & \text{local tensor-square data}\\ \hline
E_6 & 27,\,27^*
& 27\otimes27=351_A+351^{\prime}_S+27^*_S,\quad
  27\otimes27^*=1+78+650\\
E_7 & 56
& 56\otimes56=(1+1539)_A+(133+1463)_S\\
E_8 & 248
& 248\otimes248=(1+3875+27000)_S+(248+30380)_A\\
G_2 & 7
& 7\otimes7=(1+27)_S+(7+14)_A
\end{array}
\]
For $F_4$ the local root-system data certify
$\dim F_4=52$, $h^\vee=9$, and the minimal lane
$V(\omega_4)=26$, but the local engine does not certify the
$26\otimes26$ projector package.  A fundamental $\fg$-representation,
or a Drinfeld-polynomial label for a finite-dimensional Yangian module,
becomes an RTT packet only after the transfer matrix, its quadratic
relations, and its inverse-kernel relation space have been constructed
in the same presentation.
\end{proposition}

\begin{proof}
The dimensions and decompositions displayed for
$E_6,E_7,E_8$, and $G_2$ are the low-degree checks recorded by
\texttt{compute/lib/exceptional\_yangian\_engine.py}; the
Cartan and fundamental-dimension data are recorded by
\texttt{compute/lib/yangian\_rtt\_exceptional.py}.  These calculations
are representation-theoretic: they identify possible spectral
projectors for an exceptional kernel.  They neither define the Yangian
action on those projectors nor prove that the resulting quadratic
relations present $Y_\hbar(\fg)$.  The extra assertion needed for
Koszul duality is precisely the RTT relation-space identity in
Proposition~\ref{prop:exceptional-yangian-template}.
\end{proof}

\section{Per-type RTT criteria}
\label{sec:exceptional-yangian-per-type}

\begin{proposition}[$E_6$ RTT implication criterion;
\ClaimStatusProvedHere]
\label{prop:exceptional-yangian-koszul-E6}
\index{Yangian!$E_6$ Koszul duality}
For $\fg=E_6$, the implication
\[
Y_\hbar(E_6)^{!,\mathrm{ch}}\cong Y_{-\hbar}(E_6)^{\mathrm{ch}}
\]
follows from Proposition~\ref{prop:exceptional-yangian-template} after
one supplies an $E_6$ RTT/FRT presentation on the $27$ and $27^*$ lanes,
PBW in that presentation, and the inverse-kernel orthogonal-complement
identity.
Unconditionally, the local data are
\[
\dim E_6=78,\qquad h^\vee(E_6)=12,\qquad
\mathrm{Out}(E_6)\cong \Z/2,
\]
and the fundamental pair is $V(\omega_1)=27$,
$V(\omega_6)=27^*$.
\end{proposition}

\begin{proof}
The displayed root-system data are the standard $E_6$ data recorded by
the local computation and in the affine rows of
Chapter~\ref{ch:landscape-census}.  The nontrivial diagram
automorphism exchanges the two minuscule lanes.  Applying the finite
RTT criterion proves the stated Koszul-duality isomorphism precisely
when the three named $E_6$ RTT inputs have been proved in the same
presentation.
\end{proof}

\begin{remark}[$E_6$ contragredient lane]
\label{rem:exceptional-yangian-E6-outer}
The Chevalley involution sends a representation to its contragredient.
For $E_6$ this forces the $27/27^*$ distinction into the RTT kernel:
the correct comparison is between the relation space on the chosen
$27$-lane and the inverse-kernel relation space on the contragredient
lane.  The outer diagram flip is a separate symmetry; it is not a
substitute for the Chevalley lift.
\end{remark}

\begin{proposition}[$E_7$ RTT implication criterion;
\ClaimStatusProvedHere]
\label{prop:exceptional-yangian-koszul-E7}
\index{Yangian!$E_7$ Koszul duality}
For $\fg=E_7$, the implication
\[
Y_\hbar(E_7)^{!,\mathrm{ch}}\cong Y_{-\hbar}(E_7)^{\mathrm{ch}}
\]
follows from Proposition~\ref{prop:exceptional-yangian-template} after
one supplies an $E_7$ RTT/FRT presentation on the $56$-dimensional
symplectic lane, PBW in that presentation, and the inverse-kernel
orthogonal-complement identity.  Unconditionally,
\[
\dim E_7=133,\qquad h^\vee(E_7)=18,\qquad
\mathrm{Out}(E_7)=1,\qquad \dim V(\omega_7)=56.
\]
\end{proposition}

\begin{proof}
The Cartan data and the $56$-dimensional fundamental representation are
root-system facts.  The Koszul-duality statement is then exactly the
finite RTT criterion, not an additional consequence of those facts.
\end{proof}

\begin{remark}[$E_7$ symplectic self-duality]
\label{rem:exceptional-yangian-E7-self-dual}
The $56$-dimensional $E_7$ representation is symplectic self-dual.  This
settles the linear duality of the representation, but the RTT relation
space still has to be computed.  The scalar identity
$(1-\hbar P/u)^{-1}\sim 1+\hbar P/u$ for a permutation kernel is not a
proof for an exceptional universal $R$-matrix with several Casimir
eigenspaces.
\end{remark}

\begin{proposition}[$E_8$ RTT implication criterion;
\ClaimStatusProvedHere]
\label{prop:exceptional-yangian-koszul-E8}
\index{Yangian!$E_8$ Koszul duality}
For $\fg=E_8$, the implication
\[
Y_\hbar(E_8)^{!,\mathrm{ch}}\cong Y_{-\hbar}(E_8)^{\mathrm{ch}}
\]
follows from Proposition~\ref{prop:exceptional-yangian-template} after
one supplies an $E_8$ RTT/FRT presentation on the adjoint
$248$-dimensional lane, PBW in that presentation, and the
inverse-kernel orthogonal-complement identity.  Unconditionally,
\[
\dim E_8=248,\qquad h^\vee(E_8)=30,\qquad
\mathrm{Out}(E_8)=1.
\]
\end{proposition}

\begin{proof}
The adjoint representation is the smallest nontrivial $E_8$ lane in
the local computation.  Its tensor square has ambient matrix size
$248^2=61504$.  This finite size makes the orthogonal-complement
problem well-posed at each RTT level; it does not solve it.
\end{proof}

\begin{remark}[$E_8$ spectral data]
\label{rem:exceptional-yangian-E8-adjoint}
The local representation engine records
\[
248\otimes 248=1+248+3875+27000+30380.
\]
This dimension identity is necessary spectral data for an $E_8$ kernel.
The missing Koszul step is stronger:
one must show that the quadratic relation space defined by that kernel
has orthogonal complement equal to the inverse-kernel relation space.
\end{remark}

\begin{proposition}[$F_4$ RTT implication criterion;
\ClaimStatusProvedHere]
\label{prop:exceptional-yangian-koszul-F4}
\index{Yangian!$F_4$ Koszul duality}
For $\fg=F_4$, the implication
\[
Y_\hbar(F_4)^{!,\mathrm{ch}}\cong Y_{-\hbar}(F_4)^{\mathrm{ch}}
\]
follows from Proposition~\ref{prop:exceptional-yangian-template} after
one supplies an $F_4$ RTT/FRT presentation on the minimal
$26$-dimensional lane, PBW in that presentation, the
$26\otimes26$ spectral projector decomposition, and the inverse-kernel
orthogonal-complement identity.  Unconditionally,
\[
\dim F_4=52,\qquad h^\vee(F_4)=9,\qquad
\mathrm{Out}(F_4)=1,\qquad d=(1,1,2,2)
\]
for the local Cartan symmetrizer.
\end{proposition}

\begin{proof}
The symmetrizer and dimensions are local root-system data.  The compute
surface records the $F_4$ tensor-square decomposition as an uncertified
projector computation.
Therefore $F_4$ does not inherit the Koszul-duality conclusion until
that representation-theoretic input and the RTT orthogonal-complement
identity are supplied.
\end{proof}

\begin{remark}[$F_4$ folding]
\label{rem:exceptional-yangian-F4-folding}
The fixed-point identity $\fg(F_4)\cong \fg(E_6)^{\Z/2}$ is a
Lie-algebra and current-algebra statement.  A Yangian fixed-point
statement
$Y_\hbar(F_4)\cong Y_\hbar(E_6)^{\Z/2}$, compatible with finite RTT
windows and quadratic duals, is a separate descent theorem.  It cannot
be used as an independent proof until exactness of invariants and preservation
of the inverse-kernel relation spaces are proved.
\end{remark}

\begin{proposition}[$G_2$ RTT implication criterion;
\ClaimStatusProvedHere]
\label{prop:exceptional-yangian-koszul-G2}
\index{Yangian!$G_2$ Koszul duality}
For $\fg=G_2$, the implication
\[
Y_\hbar(G_2)^{!,\mathrm{ch}}\cong Y_{-\hbar}(G_2)^{\mathrm{ch}}
\]
follows from Proposition~\ref{prop:exceptional-yangian-template} after
one supplies a $G_2$ RTT/FRT presentation on the $7$-dimensional lane,
PBW in that presentation, and the inverse-kernel
orthogonal-complement identity.  Unconditionally,
\[
\dim G_2=14,\qquad h^\vee(G_2)=4,\qquad
\mathrm{Out}(G_2)=1,\qquad d=(3,1).
\]
\end{proposition}

\begin{proof}
The local rank-two engine verifies the Cartan matrix
$\bigl[\begin{smallmatrix}2&-1\\ -3&2\end{smallmatrix}\bigr]$, the
symmetrizer $d=(3,1)$, and the tensor-square dimension split
\[
7\otimes 7=(1+27)\oplus(7+14)
\]
between symmetric and alternating parts.  These data make the
$G_2$ RTT computation finite.  They do not identify the Yangian
relation space with its inverse-kernel orthogonal complement.
\end{proof}

\begin{remark}[$G_2$ triality]
\label{rem:exceptional-yangian-G2-folding}
The fixed-point identity $\fg(G_2)\cong \fg(D_4)^{\Z/3}$ is a
Lie-algebra statement.  Triality descent for Yangians would have to
commute with the RTT filtration, the finite-window truncations, and the
quadratic dual relation spaces.  Molev's classical-type PBW theorem for
$D_4$ does not by itself prove this descent.
\end{remark}

\section{The five-family obstruction theorem}
\label{sec:exceptional-yangian-five-family}

\begin{theorem}[Exceptional-type Yangian Koszul duality: exact
obligations; \ClaimStatusProvedHere]
\label{thm:exceptional-yangian-koszul-duality-all-five-types}
\index{Yangian!exceptional-type Koszul duality, five-family obstruction|textbf}
Type signature: (Open quadrant on the affine companion
$V_k(\fg)$ chart side; chain-level RTT presentation of the
filtered Yangian; Beilinson level $1\leftrightarrow 2$ quadratic
Koszul duality with reconstruction theorem Theorem~A
\textup{(}$K^2\simeq\mathrm{id}$\textup{)};
hypothesis package: the six obligations \textup{(1)}--\textup{(6)}
below, none of which is supplied by the present citation set;
finite-stage endpoint distinction: the exceptional-type Yangian PBW source is
named, never silently inherited from a classical-type result).

The bare exceptional-family statement
\[
Y_\hbar(\fg)^{!,\mathrm{ch}}
\cong
Y_{-\hbar}(\fg)^{\mathrm{ch}},
\qquad
\fg\in\{E_6,E_7,E_8,F_4,G_2\},
\]
is not proved by the sources cited in this chapter.  Precisely, for each
exceptional $\fg$, the displayed
Koszul-duality isomorphism follows once the same finite RTT/FRT
presentation satisfies the four hypotheses of
Proposition~\ref{prop:exceptional-yangian-template}.  The missing inputs
on the finite-window RTT route are exactly:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item construction of the chosen exceptional fundamental packet as an
RTT/FRT Yangian module packet, including the transfer matrix and its
quadratic relation space;
\item a correct exceptional PBW source in that same RTT/FRT
presentation;
\item the exceptional inverse-kernel orthogonal-complement computation
and scalar Laurent-gauge comparison
$R_\hbar^{-1}\sim R_{-\hbar}$ in every spectral channel;
\item compatibility of the finite-window identifications with the
stabilized Mittag--Leffler tower;
\item an ordered $E_1$ bar comparison before symmetric averaging,
identifying what part of the relation-space computation survives under
$\operatorname{Av}_N$ and what lies in $\ker\operatorname{Av}_N$;
\item for $F_4$ and $G_2$, or for any folding route, a descent theorem
showing that invariants commute with the finite RTT windows and their
quadratic dual relation spaces.
\end{enumerate}
\end{theorem}

\begin{proof}
Propositions~\ref{prop:exceptional-yangian-koszul-E6},
\ref{prop:exceptional-yangian-koszul-E7},
\ref{prop:exceptional-yangian-koszul-E8},
\ref{prop:exceptional-yangian-koszul-F4}, and
\ref{prop:exceptional-yangian-koszul-G2} prove the forward implication
from the finite RTT criterion to the five exceptional conclusions.
Proposition~\ref{thm:exceptional-yangian-pbw-grw18} proves that the
previously cited GRW input does not supply the exceptional PBW theorem.
The representation and Cartan computations in
Corollary~\ref{cor:exceptional-yangian-graded},
Proposition~\ref{prop:exceptional-fundamental-packet-scope}, and in the
five per-type criteria are necessary data, not substitutes for a Yangian
module packet, PBW, $R^\perp=R_{R^{-1}}$, or tower compatibility.
\end{proof}

\begin{corollary}[All-simple-type statement remains conditional;
\ClaimStatusProvedHere]
\label{cor:exceptional-yangian-all-simple}
\index{Yangian!Koszul duality, all simple types}
The sources cited here do not prove
\[
Y_\hbar(\fg)^{!,\mathrm{ch}}\cong
Y_{-\hbar}(\fg)^{\mathrm{ch}}
\]
for every simple complex Lie algebra $\fg$.  They prove the classical
RTT cases already covered by the local Yangian chapter and reduce the
five exceptional cases to the RTT obligations in
Theorem~\ref{thm:exceptional-yangian-koszul-duality-all-five-types}.
\end{corollary}

\begin{proof}
Molev~\cite{Molev07} supplies the classical RTT presentation and PBW
input used in the classical lanes.  The exceptional lanes require
additional RTT/FRT and inverse-kernel computations.  Since
\cite{GRW18} is orthogonal/symplectic rather than exceptional, no
all-simple corollary follows from the present citation set.
\end{proof}

\begin{remark}[Adjacent problems not decided here]
\label{rem:exceptional-yangian-does-not-close}
The obstruction theorem concerns unshifted Yangian Koszul duality in
finite RTT windows.  It does not decide the chiral quantum-group
equivalence at exceptional type, BFN Coulomb-branch interpretations of
shifted exceptional Yangians, toroidal exceptional Yangians, or elliptic
exceptional Yangians.
\end{remark}

\begin{proposition}[Drinfeld--Kohno, roots of unity, and K3 do not
promote the exceptional RTT statement; \ClaimStatusProvedHere]
\label{prop:exceptional-yangian-no-dk-root-k3-promotion}
\index{Yangian!exceptional type!non-promotion from Drinfeld--Kohno}
\index{K3!Hall--Drinfeld double versus Drinfeld Yangian}
The following proved or conditional comparison statements do not supply
any of the missing exceptional RTT inputs of
Theorem~\ref{thm:exceptional-yangian-koszul-duality-all-five-types}.
\begin{enumerate}[label=\textup{(\alph*)}]
\item The Drinfeld--Kohno theorem of
Theorem~\ref{thm:drinfeld-kohno} and the Yangian--quantum-group
deformation of Theorem~\ref{thm:yangian-quantum-group} are
affine-lineage and evaluation-locus statements.  They compare monodromy
and braiding; they do not construct an exceptional RTT/FRT presentation
or compute $R_{\leq N}^{\perp}$.
\item The root-of-unity statement
Corollary~\ref{cor:sl2-root-of-unity} is an
$\mathfrak{sl}_2$ WZW specialisation.  A Lusztig root of unity is not a
PBW theorem for $Y_\hbar(E_6)$, $Y_\hbar(E_7)$,
$Y_\hbar(E_8)$, $Y_\hbar(F_4)$, or $Y_\hbar(G_2)$.
\item The K3 object separated by the concordance is the
Hall--Drinfeld double
\[
\mathcal D_\hbar\bigl(
\mathcal Y^{\mathrm{Hall}}_\hbar(\mathrm{CoHA}_{K3\times E})
\bigr),
\]
not a Drinfeld Yangian attached to a finite-dimensional exceptional
simple Lie algebra.  The $\hbar^2=-1/8$ and
$K^{\kappa_{\mathrm{ch}}}=8$ normalization is a K3 conductor
comparison target.  It
becomes a Yangian-style statement only after the PBW-finite truncation,
parity/root fixture, and comparison map named there have been supplied.
\item Affine Yangians, toroidal Yangians, elliptic Yangians, and the
BKM denominator algebra $\mathfrak g_{\Delta_5}$ belong to the
taxonomic slots of
Proposition~\ref{prop:exceptional-yangian-type-separation}.  Their
$R$-matrices, shuffle products, or denominator identities do not
construct the ordered RTT relation space for a finite-dimensional
exceptional Drinfeld Yangian.
\end{enumerate}
\end{proposition}

\begin{proof}
Parts \textup{(a)} and \textup{(b)} are scope statements from the local
theorems cited in their text: they live on affine evaluation modules
and on the $\mathfrak{sl}_2$ root-of-unity specialization.  The
exceptional RTT theorem needs a presentation-level calculation of
relation spaces.  Part \textup{(c)} is the type separation imposed by
the concordance: the K3 construction belongs to the Hall--Drinfeld
double taxon, and its root-of-unity comparison is explicitly conditional
on finite PBW and comparison-map inputs.  None of these data equals an
exceptional inverse-kernel orthogonal-complement computation.  Part
\textup{(d)} is the same type separation applied to affine, toroidal,
elliptic, and BKM lineages.
\end{proof}

\section{Certified local data}
\label{sec:exceptional-yangian-verification}

The local compute files certify root-system and representation data, not the
exceptional Koszul theorem.
\begin{enumerate}[label=(\alph*)]
\item \emph{Cartan data.}  The exceptional dimensions, positive-root
counts, dual Coxeter numbers, and outer-automorphism orders are checked
from Cartan matrices in
\texttt{compute/lib/yangian\_rtt\_exceptional.py}.
\item \emph{Representation dimensions.}  The accessible tensor-square
decompositions for $E_6$, $E_7$, $E_8$, and $G_2$ are recorded in
\texttt{compute/lib/exceptional\_yangian\_engine.py}.  The $F_4$
$26\otimes26$ projector computation is not certified there.
\item \emph{Finite-window promotion.}  A finite matrix computation must
be repeated compatibly through the RTT tower.  The required promotion is
the stabilized Mittag--Leffler statement of
Lemma~\ref{lem:exceptional-finite-window-promotion}, not a consequence
of a single low-degree window.
\item \emph{Scalar permutation kernel.}  The identity
$(1-\hbar P/u)^{-1}\sim 1+\hbar P/u$ checks the type-A permutation
kernel up to scalar Laurent gauge.  It is not the exceptional universal
$R$-matrix computation.
\end{enumerate}

\begin{remark}[What the tests can and cannot certify]
\label{rem:exceptional-yangian-hziv}
The tests in
\texttt{compute/tests/test\_exceptional\_yangian\_koszul\_duality.py}
are valid checks for the data just listed.  They do not compute
the bar cohomology of $Y_\hbar(\fg)$, do not prove PBW for exceptional
Yangians, and do not compute $R^\perp$ for an exceptional RTT relation
space.  Therefore they cannot certify
Theorem~\ref{thm:exceptional-yangian-koszul-duality-all-five-types}
as a theorem for all five exceptional types.
\end{remark}

\section{Exceptional RTT obstructions}
\label{sec:exceptional-yangian-summary}

\begin{center}
\begin{tabular}{l|l|l|p{6.2cm}}
\textsc{type} & $\dim\fg$ & $\mathrm{Out}(\fg)$ &
\textsc{criterion}\\ \hline
$E_6$ & 78 & $\Z/2$ & $27/27^*$ packet, RTT/PBW/$R^\perp$/Mittag--Leffler obligations\\
$E_7$ & 133 & $1$ & $56$ packet, RTT/PBW/$R^\perp$/Mittag--Leffler obligations\\
$E_8$ & 248 & $1$ & $248$ packet, RTT/PBW/$R^\perp$/Mittag--Leffler obligations\\
$F_4$ & 52 & $1$ & $26$ packet plus projector certification, RTT/PBW/$R^\perp$/Mittag--Leffler obligations\\
$G_2$ & 14 & $1$ & $7$ packet plus triality descent if folding is used; RTT/PBW/$R^\perp$/Mittag--Leffler obligations\\ \hline
\multicolumn{4}{l}{\textbf{All five:}
Theorem~\ref{thm:exceptional-yangian-koszul-duality-all-five-types}
isolates the exact missing inputs.}
\end{tabular}
\end{center}

The finite-window criterion
Proposition~\ref{prop:exceptional-yangian-template} is the theorem
carried by this chapter.  Each exceptional lane requires its own
Yangian module packet, PBW theorem, ordered RTT relation space,
inverse-kernel orthogonal complement, ordered-bar comparison before
averaging, and stabilized tower compatibility in a single presentation.
