\chapter{Explicit genus expansions}\label{ch:genus-expansions}

The genus tower stops being abstract here and becomes explicit
analytical series.  Each family of chiral algebras produces a
genus-$g$ free energy $F_g(\cA)$ through the universality theorem
$\operatorname{obs}_g(\cA) = \kappa(\cA) \cdot \lambda_g$, but the
content of this chapter is not the universality theorem itself --- it
is the concrete output: generating functions whose coefficients are
Bernoulli numbers, Eisenstein series, and modular forms.  The reader
should watch how a single scalar invariant~$\kappa$ determines an
entire power series, and how that power series encodes the
$\hat{A}$-genus through the Grothendieck--Riemann--Roch pushforward.

These generating functions are the first shadows of the full modular
characteristic $\Theta_\cA$, computed in the strict model $\Convstr$
of $\Definfmod(\cA)$.  At scalar level, the genus tower is controlled
by~$\kappa(\cA)$ and the Faber--Pandharipande formula for $\lambda_g$.  The passage from a single number to an infinite
sequence of genus-dependent coefficients is not a mystery but a
mechanism: the Mumford class $\lambda_g$ supplies the universal
denominator, and the obstruction coefficient supplies the numerator.
That the resulting generating functions are classical objects ---
$x/\sin x$, the Todd genus, Bernoulli polynomials --- is evidence
that the bar-cobar machine computes invariants already visible to
algebraic topology, expressed in a new language.

The genus universality theorem
(Theorem~\ref{thm:genus-universality}) expresses the genus-$g$
obstruction as $\mathrm{obs}_g(\cA) = \kappa(\cA) \cdot \lambda_g$.
The scalar $\kappa(\cA)$ and the resulting genus expansions are now
computed for each family: Heisenberg, affine Kac--Moody, Virasoro,
and $\mathcal{W}_3$.

\begin{remark}[Three-pillar interpretation: genus expansions]
\label{rem:genus-expansions-three-pillar}
\index{genus expansion!three-pillar interpretation}
In the three-pillar architecture
(\S\ref{sec:concordance-three-pillars}):
(i)~the genus-$g$ bar complex is a \emph{curved} homotopy chiral
algebra (Theorem~\ref{thm:cech-hca}) with curvature
$\kappa(\cA) \cdot \omega_g$, where $\omega_g$ is the Mumford class
(Theorem~\ref{thm:mumford-formula}).  The secondary Borcherds
operations (Definition~\ref{def:secondary-borcherds}) at genus~$g$
encode the obstruction $\mathrm{obs}_g(\cA)$ as their leading
component: the universality theorem
$\mathrm{obs}_g = \kappa \cdot \lambda_g$ is the statement that only
the scalar shadow survives at genus~$g$;
(ii)~the genus expansion \emph{is} the weight filtration on the
modular convolution dg~Lie algebra $\mathfrak{g}^{\mathrm{mod}}_\cA$
(Definition~\ref{def:modular-convolution-dg-lie}):
the convolution $sL_\infty$-algebra
(Theorem~\ref{thm:operadic-homotopy-convolution}) acquires a
genus grading, and the free energy $F_g$ is the
genus-$g$ projection of the master MC element $\Theta_\cA$.
The generating functions $\sum_g F_g x^{2g}$ computed in this
chapter are the shadow-algebra projections of
$\Theta_\cA$ to the scalar component;
(iii)~at genus~$g \geq 2$, the bar differential uses boundary strata
of $\overline{\operatorname{FM}}_n(\Sigma_g)$; the log-FM framework
(Theorem~\ref{thm:planted-forest-tropicalization}) extends these
configuration spaces to nodal curves at the boundary of
$\overline{\mathcal{M}}_g$, and the planted-forest tropicalization
governs the clutching contributions to
$\mathrm{obs}_g$ at genus~$g$.
\end{remark}

\section{Free fields at all genera}\label{sec:free-field-genera}

\subsection{Heisenberg algebra}\label{subsec:heisenberg-all-genera}

\begin{theorem}[Heisenberg free energy at all genera;
\ClaimStatusProvedHere]\label{thm:heisenberg-all-genera}
\index{Heisenberg algebra!genus expansion}
For the Heisenberg algebra $\mathcal{H}_\kappa$
of rank~$d$ at level~$\kappa \neq 0$, the genus-$g$
free energy is:
\begin{equation}\label{eq:heisenberg-Fg}
F_g(\mathcal{H}_\kappa) = d\kappa \cdot
\frac{2^{2g-1}-1}{2^{2g-1}} \cdot
\frac{|B_{2g}|}{(2g)!}
\end{equation}
for all $g \geq 1$.  The generating function is
\begin{equation}\label{eq:heisenberg-generating}
\sum_{g=1}^{\infty} F_g(\mathcal{H}_\kappa)\, x^{2g}
= d\kappa \left(\frac{x/2}{\sin(x/2)} - 1\right).
\end{equation}
\end{theorem}

\begin{proof}
By the genus universality theorem
(Theorem~\ref{thm:genus-universality}) with
$\kappa(\mathcal{H}_\kappa) = d\kappa$
(Theorem~\ref{thm:heisenberg-obs}) and
the Faber--Pandharipande formula
(Theorem~\ref{thm:mumford-formula}).
The generating function follows from
Proposition~\ref{prop:complementarity-genus-series}.
This is the all-genera extension of the genus-$1$ computation in
\S\ref{sec:frame-genus1} and the genus tower of \S\ref{sec:frame-genus-tower}.
\end{proof}

\begin{remark}[Connection to partition functions]
\label{rem:heisenberg-partition}
The bar-complex free energy $F_g$ should not be confused with the physical partition function $Z_g$.  For a single free boson: $Z_1(\tau) = (\mathrm{Im}\,\tau)^{-1/2}|\eta(\tau)|^{-2}$ depends on all oscillator modes and the zero-mode integral, while $F_1(\mathcal{H}_1) = 1/24$ is a single obstruction number.  In general, $Z_g = [\det'(\Delta_g)]^{-1/2}$ depends on all of~$\mathcal{M}_g$, while $F_g$ extracts the single class $\kappa \cdot \lambda_g \in H^{2g}(\overline{\mathcal{M}}_g)$.
\end{remark}

\begin{remark}[Todd genus, \texorpdfstring{$\hat{A}$}{A-hat}-genus, and the universal generating function]\label{rem:a-hat-genus}
\index{Todd genus!generating function}
\index{A-hat genus@$\hat{A}$-genus!generating function}
For a single boson ($d=1$, $\kappa=1$): $1 + \sum_{g \geq 1} F_g x^{2g} = (x/2)/\sin(x/2)$, which is the $\hat{A}$-genus $(x/2)/\sinh(x/2)$ at imaginary argument, or the even part of the Todd genus:
\begin{equation}\label{eq:a-hat-identification}
\mathrm{Td}(x) = \frac{x}{1-e^{-x}} \bigg|_{x \mapsto ix} = \frac{x/2}{\sin(x/2)} \cdot e^{ix/2}.
\end{equation}
This identification reflects the family index theorem (Theorem~\ref{thm:family-index}): $F_g$ is the GRR pushforward of the Todd class.  For general $\kappa$: $\sum_g F_g x^{2g} = \kappa(\mathrm{Td}_{\mathrm{even}}(ix) - 1)$.
\end{remark}

\subsection{\texorpdfstring{$\beta\gamma$-system}{beta-gamma system}}\label{subsec:betagamma-all-genera}

\begin{proposition}[\texorpdfstring{$\beta\gamma$}{beta-gamma} genus expansion;
\ClaimStatusProvedHere]\label{prop:betagamma-all-genera}
\index{beta-gamma system@$\beta\gamma$-system!genus expansion}
For the $\beta\gamma$-system of conformal weights
$(\lambda, 1-\lambda)$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The genus-$g$ free energy is
$F_g(\beta\gamma) = \kappa(\beta\gamma) \cdot
\lambda_g^{\mathrm{FP}}$, where $\kappa(\beta\gamma)$
depends on the conformal weight~$\lambda$ via the
genus-$1$ curvature.
\item At genus $g \geq 2$, the physical partition function
\begin{equation}\label{eq:betagamma-partition}
Z_g^{\beta\gamma}(\lambda) =
\bigl[\det(\mathrm{Im}\,\Omega)\bigr]^{(1-2\lambda)(1-g)/2}
\cdot \bigl[\det'(\bar{\partial}_\lambda)\bigr]^{-1}
\end{equation}
depends on the full period matrix
$\Omega \in \mathcal{H}_g$, where
$\bar{\partial}_\lambda$ acts on sections of
$\omega_X^{\otimes \lambda}$ and the Riemann--Roch
index $\chi(\omega^{\otimes \lambda}) =
(2\lambda-1)(g-1)$ governs the zero-mode structure.
\item At genus~$1$, $Z_1^{\beta\gamma} =
|\eta(\tau)|^{-2}$ is independent of~$\lambda$
because $\omega_{E_\tau} \cong \mathcal{O}_{E_\tau}$.
\end{enumerate}
\end{proposition}

\begin{proof}
Part~(i) is a direct application of genus universality
(Theorem~\ref{thm:genus-universality}).
Part~(ii) is the standard result from the
Quillen determinant line bundle computation \cite{Quillen85}
(\ClaimStatusProvedElsewhere).
Part~(iii) follows from the triviality of the
canonical bundle on an elliptic curve.
\end{proof}

\section{Lattice VOAs at all genera}\label{sec:lattice-genera}
\index{lattice VOA!genus expansion}

The Heisenberg genus expansion (\S\ref{sec:frame-genus-tower}) was computed for a single free boson.  A lattice VOA $V_\Lambda$ tensors $d$ copies of $\mathcal{H}_1$ with the group algebra $\mathbb{C}[\Lambda]$; the lattice shifts do not change $\kappa$, so the genus expansion is a direct corollary.

\begin{theorem}[Lattice VOA free energy;
\ClaimStatusProvedHere]\label{thm:lattice-all-genera}
For a positive-definite even lattice $\Lambda$ of
rank~$d$, the lattice vertex algebra
$V_\Lambda = \mathcal{H}_1^{\otimes d} \otimes
\mathbb{C}[\Lambda]$
has genus-$g$ free energy:
\begin{equation}\label{eq:lattice-Fg}
F_g(V_\Lambda) = d \cdot
\frac{2^{2g-1}-1}{2^{2g-1}} \cdot
\frac{|B_{2g}|}{(2g)!}
\end{equation}
In particular, $F_g(V_\Lambda)$ depends only on
$\mathrm{rank}(\Lambda) = d$, not on the lattice
structure.
\end{theorem}

\begin{proof}
The lattice VOA is an extension of the rank-$d$
Heisenberg algebra $\mathcal{H}_1^{\otimes d}$ by
lattice vertex operators.  Since the lattice vertex
operators have conformal weight $\langle v, v
\rangle / 2 \geq 1$ for $v \neq 0$, they do not
contribute to the genus-$1$ curvature (which is
determined by the singular part of the OPE,
Theorem~\ref{thm:heisenberg-obs}).
Therefore $\kappa(V_\Lambda) =
\kappa(\mathcal{H}_1^{\otimes d}) = d$
(recall from \S\ref{sec:frame-genus-tower} that
$F_g(\mathcal{H}_\kappa) = \kappa \cdot \lambda_g^{\mathrm{FP}}$).
By genus universality
(Theorem~\ref{thm:genus-universality}),
$F_g(V_\Lambda) = d \cdot \lambda_g^{\mathrm{FP}}$.
\end{proof}

\begin{corollary}[Lattice-independence of genus expansion; \ClaimStatusProvedHere]
\label{cor:lattice-rank-only}
\index{lattice VOA!rank dependence}
For two positive-definite even lattices $\Lambda_1, \Lambda_2$ of the same rank $d$, the lattice VOAs $V_{\Lambda_1}$ and $V_{\Lambda_2}$ have identical genus-$g$ free energies:
\[
F_g(V_{\Lambda_1}) = F_g(V_{\Lambda_2}) = d \cdot \lambda_g^{FP}
\quad \text{for all } g \geq 1.
\]
In particular, the Leech lattice VOA $V_{\Lambda_{24}}$ and the Niemeier lattice VOA $V_{D_{24}^+}$ (both rank $24$) have the same bar-complex free energy at every genus, despite having different automorphism groups and different partition functions.
\end{corollary}

\begin{remark}[Partition functions vs.\ free energy]
\label{rem:lattice-partition-vs-free}
While $F_g$ depends only on $d = \mathrm{rank}(\Lambda)$, the physical partition function encodes the full lattice structure: $Z_g(V_\Lambda, \Omega) = \Theta_\Lambda^{(g)}(\Omega)/F_g^{\mathrm{osc}}(\Omega)$, where $\Theta_\Lambda^{(g)}$ is the degree-$g$ Siegel theta series.  For unimodular even $\Lambda$, $\Theta_\Lambda$ transforms under $\mathrm{Sp}(2g, \mathbb{Z})$ by $\det(C\Omega + D)^{d/2}$; for non-unimodular lattices, the Weil representation on $\mathbb{C}[\Lambda^*/\Lambda]$ enters.
\end{remark}

\section{\texorpdfstring{$\mathcal{W}$-algebra free energy and Higgs bundles}{$\mathcal{W}$-algebra free energy and Higgs bundles}}
\label{sec:w-algebra-genera}
\index{W-algebra@$\mathcal{W}$-algebra!genus expansion}

The progression Heisenberg $\to$ $\widehat{\mathfrak{sl}}_2$ $\to$ $\mathcal{W}$-algebra reflects increasing operadic complexity: rank~$1$ abelian (\S\ref{sec:frame-genus-tower}), rank~$1$ nonabelian (\S\ref{sec:three-theorems-sl2}), and Drinfeld--Sokolov reduction.  Since DS reduction preserves the discriminant (Theorem~\ref{thm:ds-bar-gf-discriminant}) and the modular characteristic $\kappa$, the genus expansion of a $\mathcal{W}$-algebra is determined by that of its parent Kac--Moody algebra.

\begin{theorem}[\texorpdfstring{$\mathcal{W}$}{W}-algebra free energy at all genera;
\ClaimStatusProvedHere]\label{thm:w-algebra-all-genera}
For the principal $\mathcal{W}$-algebra
$\mathcal{W}^k(\mathfrak{g})$ at generic level
$k \neq -h^\vee$, the genus-$g$ free energy is
\begin{equation}\label{eq:w-Fg-general}
F_g\bigl(\mathcal{W}^k(\mathfrak{g})\bigr)
= \kappa\bigl(\mathcal{W}^k(\mathfrak{g})\bigr)
\cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot
\frac{|B_{2g}|}{(2g)!}
\end{equation}
where $\kappa(\mathcal{W}^k(\mathfrak{g}))$ is
determined by the genus-$1$ curvature of the bar
complex and depends on the central charge via the
Drinfeld--Sokolov formula.  The complementarity sum
is
\[
\kappa\bigl(\mathcal{W}^k(\mathfrak{g})\bigr) +
\kappa\bigl(\mathcal{W}^{k'}(\mathfrak{g})\bigr)
\]
where $k' = -k - 2h^\vee$ is the Feigin--Frenkel
dual level.
\end{theorem}

\begin{proof}
Genus universality
(Theorem~\ref{thm:genus-universality}) applies
to $\mathcal{W}^k(\mathfrak{g})$ as a Koszul
chiral algebra
(Theorem~\ref{thm:w-algebra-koszul}).
The obstruction coefficient is read off from the
genus-$1$ bar complex curvature, and the
Faber--Pandharipande formula
(Theorem~\ref{thm:mumford-formula}) evaluates
the tautological integral.
\end{proof}

\begin{remark}[Connections to Higgs bundle geometry]
\label{rem:w-higgs-connections}
\index{Higgs bundle!W-algebra connection}
The $\mathcal{W}$-algebra genus expansion connects to Hitchin geometry:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Classical limit.}  The Poisson algebra underlying $\mathcal{W}^k(\mathfrak{g})$ is functions on the Hitchin base $\mathcal{B}_g(\mathfrak{g}) = \bigoplus_{i=1}^r H^0(\Sigma_g, \omega^{\otimes d_i})$.
\item \emph{Symplectic volume.}  Verlinde gives $\dim \mathbb{V}_{g,k}(G) = \int_{\mathcal{M}_{\mathrm{Higgs}}^g} \exp(k\,\omega_{\mathrm{Hitchin}})$ at leading order in~$k$.
\item \emph{AGT \textup{(\ClaimStatusConjectured; downstream of Theorem~\ref{thm:mc2-full-resolution})}:} genus-$g$ partition function of $\mathcal{W}^k(\mathfrak{g})$ equals the Nekrasov partition function of the $4$d $\mathcal{N}=2$ theory on~$\Sigma_g$.
\end{enumerate}
At critical level $k = -h^\vee$, the free energy vanishes ($\kappa = 0$); the geometric Langlands correspondence (\ClaimStatusProvedElsewhere; Gaitsgory~\cite{Gai19}) applies.
\end{remark}

\begin{conjecture}[\texorpdfstring{$\mathcal{W}_3$}{W3} bar cohomology algebraicity; \ClaimStatusConjectured]
\label{conj:w3-algebraicity}
\index{W3 algebra@$\mathcal{W}_3$!bar generating function}
The bar cohomology generating function $P_{\mathcal{W}_3}(x) = \sum_{n \geq 1} \dim H^n(\barBgeom(\mathcal{W}_3^k))\, x^n$ is an algebraic function over $\mathbb{Q}(x)$.  The first four values $2, 5, 16, 52$ are the unique solution of the depth-$2$ linear recurrence with constant term
\begin{equation}\label{eq:w3-bar-recurrence}
a(n) = 3\,a(n{-}1) + a(n{-}2) - 1, \qquad a(0) = 0,\; a(1) = 2,
\end{equation}
which yields the rational generating function
$P_{\mathcal{W}_3}(x) = x(2-3x)/\bigl((1-x)(1-3x-x^2)\bigr)$.
This predicts $\dim H^5 = 171$ and exponential growth rate
$(3+\sqrt{13})/2 \approx 3.303$.
However, four data points do not distinguish this rational function
from a degree-$2$ algebraic function with different discriminant.
If the DS discriminant principle
(Remark~\ref{rem:ds-discriminant-invariant}) holds,
the discriminant of $P_{\mathcal{W}_3}$ should match that of
$P_{\widehat{\mathfrak{sl}}_3}$; the rational candidate has
discriminant $1 - 3x - x^2$, whose compatibility with
$\widehat{\mathfrak{sl}}_3$ remains to be checked.

\emph{Scope.}  Verification requires computing $\dim H^5(\barBgeom(\mathcal{W}_3^k))$: the value $171$ would confirm the recurrence~\eqref{eq:w3-bar-recurrence}, while any other value would rule it out and point to a non-rational generating function.
\end{conjecture}

\begin{remark}[Scope]
\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~IV (computation).
The conjecture predicts the algebraicity of a specific generating function, verifiable by explicit bar cohomology computation at degree~$5$.
\end{remark}

\begin{conjecture}[Non-simply-laced discriminant; \ClaimStatusConjectured]
\label{conj:non-simply-laced-discriminant}
\index{bar complex!generating function!non-simply-laced}
For non-simply-laced Lie algebras $\mathfrak{g}$ ($B_n$, $C_n$, $F_4$, $G_2$), the bar cohomology generating function $P_{\widehat{\mathfrak{g}}}(x)$ is algebraic with discriminant $\Delta_{\mathfrak{g}}(x)$ satisfying:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\Delta_{\mathfrak{g}}$ has a simple root at $x = 1/\dim\mathfrak{g}$ (determining the exponential growth rate);
\item the DS discriminant $\Delta_{\mathcal{W}(\mathfrak{g})}$ shares the same branch locus as $\Delta_{\mathfrak{g}}$;
\item for $G_2$: $\dim\mathfrak{g} = 14$, so the predicted growth rate is $14^n$.
\end{enumerate}

\emph{Scope.}  Even for $G_2$, only three data points are available.  The chain-group dimensions are $\dim(\mathfrak{g})^n \cdot (n{-}1)! = 14, 392, 5488$ for $n = 1, 2, 3$; the \emph{bar cohomology} dimensions are not yet computed beyond $H^1 = 14$.  Computing $H^n(\barBgeom(\widehat{G}_{2,k}))$ requires the $G_2$ structure constants and is computationally demanding.
\end{conjecture}

\begin{remark}[Scope]
\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~IV (computation).
The conjecture predicts bar cohomology growth rates and discriminant structure for non-simply-laced algebras, verifiable by explicit computation of bar cohomology dimensions.
\end{remark}

\begin{conjecture}[Yangian bar generating function; \ClaimStatusConjectured]
\label{conj:yangian-bar-gf}
\index{Yangian!bar generating function}
The bar cohomology of $Y(\mathfrak{sl}_2)$ satisfies
$\dim H^n(\barBgeom(Y(\mathfrak{sl}_2))) = 3^n + 1$ for all $n \geq 1$,
with rational generating function
\begin{equation}\label{eq:yangian-bar-gf}
P_{Y(\mathfrak{sl}_2)}(x) = \frac{1 - 3x^2}{(1-x)(1-3x)}
= -1 + \frac{1}{1-x} + \frac{1}{1-3x}
\end{equation}
and recurrence $a(n) = 4\,a(n{-}1) - 3\,a(n{-}2)$ for $n \geq 3$
with $a(1) = 4$, $a(2) = 10$.

\emph{Evidence.}  Three data points ($4, 10, 28$) match $3^n + 1$ exactly.
The partial fraction decomposition $-1 + 1/(1{-}x) + 1/(1{-}3x)$ is
consistent with the following conjectural decomposition
(\ClaimStatusConjectured): a ``constant'' contribution (from the
$\mathfrak{gl}_1$ center) and a ``$3^n$'' contribution (from the
$\mathfrak{sl}_2$ factor).  At degree~$1$, the chiral bar complex
of $Y(\mathfrak{sl}_2)$ matches
that of $\widehat{\mathfrak{gl}}_2 \cong \widehat{\mathfrak{sl}}_2
\times \widehat{\mathfrak{gl}}_1$ via the K\"unneth formula (cf.\
Remark~\ref{rem:yangian-gl2-kunneth}).  At degree~$2$, the Yangian
already exceeds the K\"unneth prediction
($H^2(Y) = 10$ vs.\ $H^2(\widehat{\mathfrak{gl}}_2) = 9$);
at degree~$3$, the gap widens to $28 - 24 = 4$.  The formula
predicts $\dim H^4 = 82$ and $\dim H^5 = 244$.

\emph{Scope.}  Three data points do not uniquely determine the generating
function; the value $\dim H^4 = 82$ is the critical test.
The rationality of $P_{Y(\mathfrak{sl}_2)}$ would be striking, since
$\Einf$-chiral algebras typically have algebraic (but not rational)
bar generating functions (Corollary~\ref{cor:algebraicity-koszul}).
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\end{conjecture}

\begin{remark}[Scope]
\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~IV (computation).
The conjecture predicts the rational form of the Yangian bar generating function, testable by computing $\dim H^4(\barBgeom(Y(\mathfrak{sl}_2)))$.
\end{remark}

\section{\texorpdfstring{Three theorems in action: $\widehat{\mathfrak{sl}}_2$ at all genera}{Three theorems in action: affine sl2 at all genera}}\label{sec:three-theorems-sl2}
\index{three theorems!sl2 showcase@$\mathfrak{sl}_2$ showcase}
\index{genus expansion!sl2@$\mathfrak{sl}_2$}

We trace all three main theorems through a single example: the affine Kac--Moody algebra $\widehat{\mathfrak{sl}}_{2,k}$ at generic level~$k$, computing the genus-$g$ invariants explicitly.  Where the Heisenberg algebra (\S\ref{sec:frame-genus-tower}) was the abelian prototype --- genus expansion controlled by a single number $\kappa = k$ --- $\widehat{\mathfrak{sl}}_2$ is the first \emph{nonabelian} case, introducing structure constants and dual Coxeter corrections.

\subsection{Setup}\label{subsec:sl2-genus-setup}

Recall from the Master Table (Table~\ref{tab:master-invariants}) the Koszul duality data for $\widehat{\mathfrak{sl}}_2$:
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lllll}
\toprule
Algebra & Koszul Dual & $c(\cA)$ & $c + c'$ & $\kappa(\cA)$ \\
\midrule
$\widehat{\mathfrak{sl}}_{2,k}$ & $\widehat{\mathfrak{sl}}_{2,-k-4}$ & $\dfrac{3k}{k+2}$ & $6$ & $\dfrac{3(k+2)}{4}$ \\[6pt]
\bottomrule
\end{tabular}
\end{center}
The Feigin--Frenkel involution $k \mapsto k' = -k - 2h^\vee = -k-4$ acts on the central charge as $c \mapsto c' = 6 - c$, and on the obstruction coefficient as $\kappa \mapsto -\kappa$.

\begin{itemize}
\item \emph{Theorem~A} (Geometric Bar-Cobar Duality, Theorem~\ref{thm:bar-cobar-isomorphism-main}; this is Theorem~$\mathrm{A}_2$ in the $\mathrm{A}_0/\mathrm{A}_1/\mathrm{A}_2$ decomposition of Remark~\ref{rem:theorem-A-decomposition}):
$(\widehat{\mathfrak{sl}}_{2,k})^! \simeq
\widehat{\mathfrak{sl}}_{2,-k-4}$ via bar construction and Verdier
duality on configuration space integrals.  The bar coalgebra
$\bar{B}(\widehat{\mathfrak{sl}}_{2,k})$ is a factorization
coalgebra on~$\mathrm{Ran}(X)$; Verdier duality
on~$\overline{C}_n(X)$ exchanges it with
$\bar{B}(\widehat{\mathfrak{sl}}_{2,-k-4})$, geometrically
implementing the Feigin--Frenkel involution
$k \mapsto -k - 2h^\vee$.  The level shift arises because the bar differential decomposes
into bracket (simple pole) and curvature (double pole, proportional
to the Killing form); Verdier duality on~$\overline{C}_n(X)$
negates the level and adds the dual Coxeter
correction~$h^\vee$.
\item \emph{Theorem~B} (Bar-Cobar Inversion, Theorem~\ref{thm:higher-genus-inversion}):
For $k \neq -2$, the genus-$g$ spectral sequence collapses at $E_2$; at critical level $k = -2$, the inversion $\Omega(\bar{B}(\widehat{\mathfrak{sl}}_{2,-2})) \xrightarrow{\sim} \widehat{\mathfrak{sl}}_{2,-2}$ is strict.
\item \emph{Theorem~C} (Complementarity, Theorem~\ref{thm:quantum-complementarity-main}):
$\mathrm{obs}_g(\widehat{\mathfrak{sl}}_{2,k}) + \mathrm{obs}_g(\widehat{\mathfrak{sl}}_{2,-k-4}) = 0$ in $H^{2g}(\overline{\mathcal{M}}_g)$ for all~$g$.
\end{itemize}

All three theorems are unconditional for $\widehat{\mathfrak{sl}}_{2,k}$
at generic level: the PBW spectral sequence degenerates at every
genus by Theorem~\ref{thm:pbw-allgenera-km}.  The proof mechanism is
representation-theoretic: the genus-$g$ enrichment from
$H^1(\Sigma_g)$ decomposes under the adjoint action of
$\mathfrak{sl}_2$, and Whitehead's theorem eliminates all non-trivial
summands.  At conformal weight~$2$, this is the decomposition
$\mathfrak{sl}_2^{\otimes 2} = V_5 \oplus V_3 \oplus V_1$---the
bracket kills~$V_3$, Whitehead kills~$V_5$, and the
level-$k$ Killing contraction kills~$V_1$.
The genus expansion below
is the numerical shadow of this algebraic mechanism.

\subsection{\texorpdfstring{Genus-$g$ free energy}{Genus-g free energy}}\label{subsec:sl2-free-energy}

\begin{theorem}[\texorpdfstring{$\widehat{\mathfrak{sl}}_2$}{sl-hat_2} free energy at all genera;
\ClaimStatusProvedHere]\label{thm:sl2-all-genera}
\textup{[Regime: curved-central\textup{;}
Convention~\textup{\ref{conv:regime-tags}}.]}

For $\widehat{\mathfrak{sl}}_{2,k}$ at generic level $k \neq -2$, the genus-$g$ free energy is:
\begin{equation}\label{eq:sl2-Fg}
F_g(\widehat{\mathfrak{sl}}_{2,k}) = \frac{3(k+2)}{4} \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}
\end{equation}
where $B_{2g}$ are the Bernoulli numbers ($B_2 = \frac{1}{6}$, $B_4 = -\frac{1}{30}$, $B_6 = \frac{1}{42}$, $B_8 = -\frac{1}{30}$, $B_{10} = \frac{5}{66}$).
\end{theorem}

\begin{proof}
By the genus universality theorem (Theorem~\ref{thm:genus-universality}), the genus-$g$ obstruction class factors as $\mathrm{obs}_g(\cA) = \kappa(\cA) \cdot \lambda_g$, where $\lambda_g = c_g(\mathbb{E})$ is the top Chern class of the Hodge bundle on $\overline{\mathcal{M}}_g$.  For $\widehat{\mathfrak{sl}}_{2,k}$, the genus-1 curvature computation (Theorem~\ref{thm:sl2-genus1-curvature}) gives $\kappa = 3(k+2)/4$.

The free energy is the tautological integral:
\[
F_g(\cA) = \int_{\overline{\mathcal{M}}_{g,1}} \psi_1^{2g-2}\, \mathrm{obs}_g(\cA) = \kappa(\cA) \cdot \int_{\overline{\mathcal{M}}_{g,1}} \psi_1^{2g-2}\, \lambda_g
\]
The Faber--Pandharipande formula (Theorem~\ref{thm:mumford-formula}) evaluates the integral:
\[
\int_{\overline{\mathcal{M}}_{g,1}} \psi_1^{2g-2}\, \lambda_g = \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}
\]
Substituting $\kappa = 3(k+2)/4$ yields~\eqref{eq:sl2-Fg}.
\end{proof}

\begin{computation}[Explicit values through \texorpdfstring{$g = 10$}{g = 10}]\label{comp:sl2-genus-table}
Evaluating~\eqref{eq:sl2-Fg} for the first ten genera.
For $g = 1, \ldots, 5$, we list the full data:

\medskip
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{cccccc}
\toprule
$g$ & $|B_{2g}|$ & $\lambda_g^{FP}$ & $F_g$ (general $k$) & $F_g$ ($k=1$) & $F_g$ ($k=2$)  \\
\midrule
$1$ & $\frac{1}{6}$ & $\frac{1}{24}$ & $\frac{k+2}{32}$ & $\frac{3}{32}$ & $\frac{1}{8}$  \\[6pt]
$2$ & $\frac{1}{30}$ & $\frac{7}{5760}$ & $\frac{7(k+2)}{7680}$ & $\frac{7}{2560}$ & $\frac{7}{1920}$  \\[6pt]
$3$ & $\frac{1}{42}$ & $\frac{31}{967680}$ & $\frac{31(k+2)}{1290240}$ & $\frac{31}{430080}$ & $\frac{31}{322560}$  \\[6pt]
$4$ & $\frac{1}{30}$ & $\frac{127}{154828800}$ & $\frac{127(k+2)}{206438400}$ & $\frac{127}{68812800}$ & $\frac{127}{51609600}$  \\[6pt]
$5$ & $\frac{5}{66}$ & $\frac{73}{3503554560}$ & $\frac{73(k+2)}{4671406080}$ & $\frac{73}{1557135360}$ & $\frac{73}{1167851520}$  \\[4pt]
\bottomrule
\end{tabular}
\end{center}

\medskip
\noindent
For $g = 6, \ldots, 10$, we list $\lambda_g^{FP}$ and the coefficient
$F_g/(k{+}2) = \frac{3}{4}\lambda_g^{FP}$:

\medskip
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{cccc}
\toprule
$g$ & $|B_{2g}|$ & $\lambda_g^{FP}$ & $F_g/(k{+}2)$ \\
\midrule
$6$ & $\frac{691}{2730}$ & $\frac{1414477}{2678117105664000}$ & $\frac{1414477}{3570822807552000}$ \\[6pt]
$7$ & $\frac{7}{6}$ & $\frac{8191}{612141052723200}$ & $\frac{8191}{816188070297600}$ \\[6pt]
$8$ & $\frac{3617}{510}$ & $\frac{16931177}{49950709902213120000}$ & $\frac{16931177}{66600946536284160000}$ \\[6pt]
$9$ & $\frac{43867}{798}$ & $\frac{5749691557}{669659197233029971968000}$ & $\frac{5749691557}{892878929644039962624000}$ \\[6pt]
$10$ & $\frac{174611}{330}$ & $\frac{91546277357}{420928638260761696665600000}$ & $\frac{91546277357}{561238184347682262220800000}$ \\[4pt]
\bottomrule
\end{tabular}
\end{center}

\medskip
\noindent
In each case, $F_g$ is a linear function of~$k$, reflecting the factored form $F_g = \frac{3}{4}(k+2) \cdot \lambda_g^{FP}$.  At critical level $k = -2$, every entry vanishes: $F_g(\widehat{\mathfrak{sl}}_{2,-2}) = 0$ for all~$g$.  The super-exponential decay $\lambda_g^{FP} \sim 2/(2\pi)^{2g}$ (cf.\ Proposition~\ref{prop:fp-coefficients}) ensures that the genus expansion $\sum_g F_g$ converges for all $k \neq -2$.
\end{computation}

\begin{computation}[The $\widehat{\mathfrak{sl}}_2$ shadow tower at
$k = 1$: from OPE to Weyl detection]
\label{comp:sl2-shadow-tower}
\index{sl2@$\widehat{\mathfrak{sl}}_2$!shadow tower}
We build the full shadow machine for
$\widehat{\mathfrak{sl}}_{2,1}$ from its OPE.

\medskip\noindent\textbf{Step 1: OPE data.}
$J^a(z)J^b(w) \sim \frac{(k+2)\kappa^{ab}}{(z-w)^2}
+ \frac{f^{ab}{}_c J^c(w)}{z-w}$
with $k = 1$, $h^\vee = 2$, $k_{\mathrm{eff}} = 3$.  For $\mathfrak{sl}_2$:
$[e,f] = h$, $[h,e] = 2e$, $[h,f] = -2f$,
$\kappa(e,f) = 1$, $\kappa(h,h) = 2$.

\medskip\noindent\textbf{Step 2: Hessian.}
$H_{\mathrm{aff}} = 3\kappa$ on $\mathfrak{sl}_2[1]$.
Propagator $P = (1/3)\kappa^{-1}$.

\medskip\noindent\textbf{Step 3: Cubic shadow.}
From the simple pole:
$\mathfrak{C}_{\mathrm{aff}}(x,y,z) = \kappa(x,[y,z])$.
The cubic Hamiltonian is
$\frac{1}{6}\kappa(a,[a,a])$.  For $a = \alpha e + \beta f + \gamma h$:
\[
[a,a] = 2(\alpha\beta - \beta\alpha)[e,f] + \cdots
= 2\alpha\beta h + 2\alpha\gamma \cdot 2e + 2\beta\gamma\cdot(-2f)
+ \cdots
\]
Since $[a,a] = 0$ for commutative scalars, the cubic vanishes on
one-dimensional slices but is nonzero on the full $3$-dimensional
space.

\medskip\noindent\textbf{Step 4: Quartic obstruction = 0 by Jacobi.}
The $s$-channel on input $(e,f,e,f)$:
$\kappa([e,f],[e,f])/3 = \kappa(h,h)/3 = 2/3$.
The $u$-channel:
$\kappa([e,f],[f,e])/3 = \kappa(h,-h)/3 = -2/3$.
Sum: $2/3 + 0 + (-2/3) = 0$.
This is the Jacobi identity in action.

\medskip\noindent\textbf{Step 5: Complementarity potential.}
$S_{\widehat{\mathfrak{sl}}_{2,1}}(a) = \frac{3}{2}\kappa(a,a)
+ \frac{1}{6}\kappa(a,[a,a])$.
This is \textbf{polynomial}: the potential terminates at cubic order.
The shadow tower terminates at arity~$3$ --- the Lie/tree archetype.

\medskip\noindent\textbf{Step 6: Critical level $k = -2$.}
$H = 0$, $\mathfrak{C} = \kappa(a,[a,a])$ survives.
$S_{\mathrm{crit}}(a) = \frac{1}{6}\kappa(a,[a,a])$,
$\operatorname{Crit}(S_{\mathrm{crit}}) = \{a : [a,a] = 0\}$
--- the flat connections, i.e., the oper space
(Theorem~\ref{thm:oper-bar}).

\medskip\noindent\textbf{Step 7: Genus loop.}
$\Lambda_P(\mathfrak{C})(x)
= (1/3)\sum_a \kappa(x,[e_a,e^a])$.
For $\mathfrak{sl}_2$:
$\sum_a [e_a,e^a] = [e,f] + [f,e] + \frac{1}{2}[h,h]
= h - h + 0 = 0$.
So $\Lambda_P(\mathfrak{C}) = 0$: the genus-$1$ correction from
the cubic shadow vanishes for $\mathfrak{sl}_2$.  The scalar
genus tower $F_g = (3/4)(k+2)\lambda_g^{\mathrm{FP}}$ carries
all the modular information.

\medskip\noindent\textbf{Step 8: Phase index.}
$\nu_{\mathrm{nl}}(\widehat{\mathfrak{sl}}_{2,1}) = 3$: the cubic
is the leading nonlinear jet.  At critical level $k = -2$, the
index remains $3$ but the Hessian degenerates, forcing the modular
geometry to probe the cubic term.
\end{computation}

\subsection{Complementarity at every genus}\label{subsec:sl2-complementarity}

For the Heisenberg algebra, complementarity was the identity $\kappa(\mathcal{H}_k) + \kappa(\mathcal{H}_{-k}) = 0$ (\S\ref{sec:frame-complementarity}).  The mechanism is the same here --- $\kappa + \kappa' = 0$ for all affine Kac--Moody --- but the dual level $k' = -k - 2h^\vee$ now involves the dual Coxeter number.

\begin{proposition}[\texorpdfstring{$\widehat{\mathfrak{sl}}_2$}{sl2-hat} complementarity; \ClaimStatusProvedHere]\label{prop:sl2-complementarity-all-genera}
For all $g \geq 1$ and all $k \neq -2$:
\begin{equation}\label{eq:sl2-complementarity-allgenera}
F_g(\widehat{\mathfrak{sl}}_{2,k}) + F_g(\widehat{\mathfrak{sl}}_{2,-k-4}) = 0
\end{equation}
\end{proposition}

\begin{proof}
The obstruction coefficients satisfy:
\[
\kappa(\widehat{\mathfrak{sl}}_{2,k}) + \kappa(\widehat{\mathfrak{sl}}_{2,-k-4}) = \frac{3(k+2)}{4} + \frac{3(-k-4+2)}{4} = \frac{3(k+2)}{4} + \frac{3(-k-2)}{4} = 0
\]
Since $F_g$ is linear in $\kappa$, the result follows.
\end{proof}

\begin{remark}[Comparison with Virasoro complementarity]\label{rem:sl2-vs-vir-complementarity}
For $\widehat{\mathfrak{sl}}_2$, the obstruction coefficients cancel exactly ($\kappa + \kappa' = 0$), a consequence of the symmetric level-shift $k \mapsto -k-4$ fixing the midpoint $k = -2$.  For the Virasoro algebra $\mathrm{Vir}_c \simeq \mathcal{W}^k(\mathfrak{sl}_2)$, the complementarity takes a different form:
\[
\kappa(\mathrm{Vir}_c) + \kappa(\mathrm{Vir}_{26-c}) = \frac{c}{2} + \frac{26-c}{2} = 13
\]
so $F_g(\mathrm{Vir}_c) + F_g(\mathrm{Vir}_{26-c}) = 13 \cdot \lambda_g^{\mathrm{FP}}$, where $\lambda_g^{\mathrm{FP}} = \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}$.  The nonzero sum $\kappa + \kappa' = 13$ reflects the conformal anomaly of the $c = 26$ bosonic string: the combined obstruction of Virasoro and its same-family shadow partner equals half the bosonic string central charge times $\lambda_g^{\mathrm{FP}}$.

For the $\mathcal{W}_3$ algebra (where $c + c' = 100$), the analogous computation gives $\kappa + \kappa' = 250/3$.
\end{remark}

\begin{remark}[Verlinde bundle and the limits of the scalar genus tower]%
\label{rem:verlinde-vs-kappa}%
\index{Verlinde formula!vs scalar genus tower}%
The free energy $F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$ is the
\emph{Euler characteristic} of a much richer object.  For
$\widehat{\mathfrak{sl}}_{2,k}$ at integrable level, the
factorization homology $\int_{\Sigma_g}\!\widehat{\mathfrak{sl}}_{2,k}$
is a vector bundle over $\mathcal{M}_g$---the \emph{Verlinde bundle}
(or bundle of conformal blocks)---whose rank is given by the
Verlinde formula
(equation~\eqref{eq:verlinde-general}):
\[
\dim V_{g,k}(\mathfrak{sl}_2)
\;=\; \sum_{\lambda=0}^{k} \left(\frac{S_{0\lambda}}{S_{00}}\right)^{2-2g},
\qquad S_{j\ell} = \sqrt{\tfrac{2}{k+2}}
\sin\!\left(\tfrac{\pi(j+1)(\ell+1)}{k+2}\right).
\]
At genus~$1$ this gives $k{+}1$; at genus~$2$ it
grows as a polynomial in~$k$.

Theorem~D sees a single scalar:
$\kappa = 3(k{+}2)/4$.  This is the first Chern class of the
Verlinde bundle (via the Quillen determinant formula);
it cannot distinguish $k = 5$ (rank $6$, rich representation
theory) from any other algebra sharing
$\kappa = 21/4$.

The corrected bar cohomology $H^*(\barB^{(g)}(\widehat{\mathfrak{sl}}_{2,k}), \Dg{g})$
(Remark~\ref{rem:four-levels}) should recover the rank of the
Verlinde bundle---the first concrete test
that the bar complex at genus~$g$ encodes representation-theoretic
data beyond the scalar genus tower.
The variation of this cohomology over $\mathcal{M}_g$
gives the KZ/Hitchin flat connection, and its monodromy
gives the mapping class group representation on
conformal blocks.

\smallskip\noindent
\emph{Resolution.}
Theorem~\ref{thm:bar-cohomology-level-independence} resolves
the fiberwise genus-independence question at integrable levels:
since $\lambda = k + h^\vee > 0$ for $k \ge 1$, integrable
levels are \emph{outside} the exceptional set~$\Sigma_n$
and hence generic (Proposition~\ref{prop:integrable-level-independence}).
The two Verlinde normalizations are reconciled in
Remark~\ref{rem:two-verlinde-normalizations}.
\end{remark}

\begin{proposition}[Level-independence at integrable levels; \ClaimStatusProvedElsewhere]%
\label{prop:integrable-level-independence}%
\index{level-independence!integrable levels}%
\index{bar complex!level-independence!integrable}%
For any simple~$\mathfrak{g}$ and degree~$n$,
Theorem~\textup{\ref{thm:bar-cohomology-level-independence}} shows that
the bar cohomology dimension $\dim H^n(\barB^\bullet(\widehat{\mathfrak{g}}_k))$
is constant for $\lambda = k + h^\vee$ outside a finite exceptional set~$\Sigma_n$.
At integrable levels $k \in \mathbb{Z}_{\ge 1}$, the shifted parameter
$\lambda = k + h^\vee \ge 1 + h^\vee > 0$, which lies outside~$\Sigma_n$
(whose only element for $\mathfrak{sl}_2$ at degree~$2$ is $\lambda = 0$).
In particular:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The fiberwise bar cohomology dimensions at integrable levels
  equal the generic-level values---no modification from null-state
  truncation occurs at the bar cohomology level.
\item PBW concentration (Theorem~\textup{\ref{thm:pbw-universal-semisimple}})
  applies at integrable levels, so the bar cohomology is
  genus-independent there as well.
\item The Verlinde bundle rank is recovered not by a change in bar
  cohomology dimensions, but by the chain-level modular functor
  structure (Remark~\textup{\ref{rem:four-levels}}, Level~$1$).
\end{enumerate}
\end{proposition}

\begin{remark}[Two Verlinde normalizations]%
\label{rem:two-verlinde-normalizations}%
\index{Verlinde formula!normalization conventions}%
The Verlinde formula admits two standard normalizations
that must not be conflated:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Normalized partition function.}
  $Z_g = \sum_{\lambda=0}^{k} (S_{0\lambda}/S_{00})^{2-2g}$,
  the formula appearing in~\eqref{eq:verlinde-general}.
  This equals $k{+}1$ at genus~$1$ but is generically
  non-integer for $g \ge 2$ (e.g., $Z_2 = 5/2$ for
  $\mathfrak{sl}_2$ at $k = 2$).
\item \emph{Integer conformal block dimension
  \textup{(}Beauville normalization\textup{)}.}
  $\dim V_{g,k} = Z_g \cdot S_{00}^{\,2-2g}$,
  equivalently
  \[
    \dim V_{g,k}(\mathfrak{sl}_2)
    \;=\; \Bigl(\frac{k{+}2}{2}\Bigr)^{\!g-1}
    \sum_{j=0}^{k}
    \sin^{2-2g}\!\Bigl(\frac{\pi(j{+}1)}{k{+}2}\Bigr),
  \]
  which is always a positive integer.
\end{enumerate}
The relationship $\dim V = Z_g \cdot S_{00}^{\,2-2g}$
reconciles the non-integer $Z_g$ with the integer
conformal block count.
The scalar genus tower $F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$
(Theorem~D) is the first Chern class of the Verlinde bundle;
$\dim V_{g,k}$ is its rank.  Both are well-defined and consistent,
but they encode different data.
\end{remark}

\begin{proposition}[Bivariate generating function; \ClaimStatusProvedHere]
\label{prop:bivariate-gf}
\index{generating function!bivariate}
The full genus-expanded free energy of $\widehat{\mathfrak{sl}}_{2,k}$ has a closed-form bivariate generating function in the genus variable $x$ and the level variable $t = k + 2$:
\begin{equation}\label{eq:bivariate-gf}
\sum_{g=1}^{\infty} F_g(\widehat{\mathfrak{sl}}_{2,k})\, x^{2g} = \frac{3t}{4}\left(\frac{x/2}{\sin(x/2)} - 1\right).
\end{equation}
This is linear in $t$ (hence in $k$) and is the product of the algebra-dependent factor $3t/4 = \kappa$ with the universal generating function $\hat{A}(x) - 1$.  For any Koszul chiral algebra, the analogous formula is
\begin{equation}\label{eq:bivariate-gf-general}
\sum_{g=1}^{\infty} F_g(\cA)\, x^{2g} = \kappa(\cA) \cdot \left(\frac{x/2}{\sin(x/2)} - 1\right).
\end{equation}
The bivariate structure reflects the factorization $F_g = \kappa \cdot \lambda_g^{FP}$ (Theorem~\ref{thm:genus-universality}).
\end{proposition}

\begin{proof}
Substituting $F_g = \kappa \cdot \lambda_g^{FP}$ into the series and using the classical identity
\[
\sum_{g \geq 1} \lambda_g^{FP}\, x^{2g} = \frac{x}{2\sin(x/2)} - 1,
\]
which follows from the generating function for Bernoulli numbers:
\[
\sum_{g \geq 1} \frac{(2^{2g-1}-1)|B_{2g}|}{(2g)!}\, x^{2g} = \frac{x}{2\sin(x/2)} - 1. \qedhere
\]
\end{proof}

\subsection{Explicit genus-2 bar differential}\label{subsec:sl2-genus2-bar}
\index{bar complex!genus-2 differential}
\index{sl2@$\mathfrak{sl}_2$!genus-2 bar differential}

The genus-1 curvature of $\widehat{\mathfrak{sl}}_{2,k}$ was computed in
Theorem~\ref{thm:sl2-genus1-curvature} by extracting the B-cycle
monodromy of the elliptic propagator.  The analogous
computation at genus~$2$ yields the first \emph{non-abelian} genus-$2$ bar
differential.  The Heisenberg case
(Theorem~\ref{thm:heisenberg-genus2-obstruction}; see also the
frame computation in \S\ref{sec:frame-genus2}) serves as template;
the new content is the interplay between the double-pole
coefficient~$k$ and the structure constants~$f^{ab}{}_c$, which
produces the dual Coxeter correction $h^\vee = 2$ in the curvature.

\subsubsection{Genus-2 propagator for affine Kac--Moody algebras}

\begin{proposition}[Non-abelian genus-2 propagator; \ClaimStatusProvedHere]
\label{prop:km-genus2-propagator}
\index{propagator!genus-2 non-abelian}
Let $\widehat{\mathfrak{g}}_k$ be an affine Kac--Moody algebra on a
genus-$2$ surface $\Sigma_2$ with period matrix
$\Omega \in \mathfrak{H}_2$ and normalized abelian differentials
$\omega_1, \omega_2$.  The genus-$2$ OPE propagator is:
\begin{equation}\label{eq:km-genus2-ope}
J^a(z) J^b(w) \sim
  k\,\kappa^{ab} \cdot \bigl(-\partial_w K^{(2)}(z,w|\Omega)\bigr)
  + f^{ab}{}_{c}\, J^c(w) \cdot K^{(2)}(z,w|\Omega)
\end{equation}
where $K^{(2)}(z,w|\Omega) = \partial_z \log E(z,w;\Omega)$
is the genus-$2$ chiral propagator
\textup{(}Definition~\textup{\ref{def:prime-form-g2})},
$\kappa^{ab} = (J^a, J^b)$ is the normalized Killing form,
and $f^{ab}{}_c$ are the structure constants.
The B-cycle monodromies are:
\begin{align}
K^{(2)}(z + \delta_{B_j}, w|\Omega)
  &= K^{(2)}(z, w|\Omega) - 2\pi i\, \omega_j(w)
  \label{eq:km-genus2-K-mono} \\
\partial_w K^{(2)}(z + \delta_{B_j}, w|\Omega)
  &= \partial_w K^{(2)}(z, w|\Omega) - 2\pi i\, \partial_w\omega_j(w)
  \label{eq:km-genus2-dK-mono}
\end{align}
for $j = 1, 2$.
\end{proposition}

\begin{proof}
The OPE~\eqref{eq:km-genus2-ope} is the standard replacement of the
flat-space propagator $1/(z-w)$ by the genus-$2$ propagator $K^{(2)}$:
the double pole $k\,\kappa^{ab}/(z-w)^2 = -k\,\kappa^{ab}\,\partial_w[1/(z-w)]$
becomes $-k\,\kappa^{ab}\,\partial_w K^{(2)}$, and the simple pole
$f^{ab}{}_c J^c(w)/(z-w)$ becomes $f^{ab}{}_c J^c(w) \cdot K^{(2)}$.
The B-cycle monodromy~\eqref{eq:km-genus2-K-mono} is
equation~\eqref{eq:genus2-B-quasi} from the Heisenberg computation.
Equation~\eqref{eq:km-genus2-dK-mono} follows by differentiation.
\end{proof}

\begin{remark}[Genus-1 vs genus-2 monodromies]\label{rem:g1-g2-mono-contrast}
At genus~$1$, the single B-cycle monodromy of $K^{(1)}$ is the
\emph{constant} $-2\pi i$, so $\partial_w K^{(1)}$ is doubly periodic
and only the simple-pole term contributes to the curvature.  At
genus~$2$, both B-cycle monodromies are \emph{function-valued}
(proportional to the abelian differentials $\omega_j$), so
$\partial_w\omega_j \neq 0$ in general and the \emph{double-pole term
also acquires a monodromy defect}.  This is the mechanism by which the
level~$k$ enters the genus-$2$ curvature directly, in addition to the
dual Coxeter correction from the structure constants.
\end{remark}

\subsubsection{\texorpdfstring{The differential $d^{(2)}$ on $\bar{B}(\widehat{\mathfrak{sl}}_{2,k})$}{The differential d-two on the affine sl2 bar complex}}

\begin{theorem}[Genus-2 bar differential for \texorpdfstring{$\widehat{\mathfrak{sl}}_2$}{sl-hat_2};
\ClaimStatusProvedHere]\label{thm:sl2-genus2-bar-differential}
\index{bar complex!genus-2 for sl2@genus-2 for $\mathfrak{sl}_2$}
Fix a basis $\{e, f, h\}$ of $\mathfrak{sl}_2$ with
$[e,f] = h$, $[h,e] = 2e$, $[h,f] = -2f$, and Killing form
$\kappa^{ef} = \kappa^{fe} = 1$, $\kappa^{hh} = 2$
\textup{(}all other entries zero\textup{)}.
The genus-$2$ component of the bar differential,
$d^{(2)}\colon \bar{B}^n(\widehat{\mathfrak{sl}}_{2,k}) \to
\bar{B}^{n-1}(\widehat{\mathfrak{sl}}_{2,k})$, is determined by its
action on degree-$2$ elements:
\begin{equation}\label{eq:sl2-d2-formula}
d^{(2)}\bigl(J^a \boxtimes J^b \cdot \eta_{12}\bigr)
= \sum_{j=1}^{2} \Bigl[
  -2\pi i \cdot k\,\kappa^{ab}\, \partial_w\omega_j
  \;+\; (-2\pi i) \cdot f^{ab}{}_{c}\, J^c \cdot \omega_j
\Bigr] \otimes [\beta_j]
\end{equation}
where $[\beta_j] \in H_1(\Sigma_2, \mathbb{Z})$ denotes the
cohomology class dual to the $j$-th B-cycle monodromy, and
$\omega_j$ is the $j$-th normalized abelian differential.
\end{theorem}

\begin{proof}
The bar differential at genus~$g$ decomposes as
$d = d^{(0)} + d^{(1)} + d^{(2)} + \cdots$
(Theorem~\ref{thm:genus-differential}).  The component $d^{(2)}$ is
the genus-$2$ correction arising from the B-cycle monodromies of the
propagator on~$\Sigma_2$.

\emph{Step~1: Double-pole contribution.}
The double-pole OPE $k\,\kappa^{ab}\, (-\partial_w K^{(2)})$ acquires
B-cycle monodromy $-2\pi i\, k\,\kappa^{ab}\, \partial_w\omega_j$
via~\eqref{eq:km-genus2-dK-mono}.  At genus~$1$, the analogous
monodromy $\partial_w\omega_\tau$ vanishes because $\omega_\tau = dz$
is constant on the elliptic curve, so the double pole does not
contribute to the genus-$1$ curvature.  At genus~$2$, the abelian
differentials $\omega_j$ are non-constant holomorphic sections of
$\omega_{\Sigma_2}$, so $\partial_w\omega_j \neq 0$ and the double
pole contributes.

\emph{Step~2: Simple-pole contribution.}
The simple-pole OPE $f^{ab}{}_c\, J^c \cdot K^{(2)}$ acquires
B-cycle monodromy $-2\pi i\, f^{ab}{}_c\, J^c \cdot \omega_j$
via~\eqref{eq:km-genus2-K-mono}.  This is identical in form to the
Heisenberg contribution (with $f^{ab}{}_c\, J^c$ replacing the abelian
level~$\kappa$) and is the mechanism by which the structure constants
of~$\mathfrak{sl}_2$ enter the genus-$2$ bar differential.

\emph{Step~3: Assembly.}
Summing over both B-cycles $j = 1, 2$
gives~\eqref{eq:sl2-d2-formula}.  The first term is proportional to the
level~$k$ and the Killing form~$\kappa^{ab}$ (the ``double-pole
channel''); the second is proportional to the structure
constants~$f^{ab}{}_c$ (the ``simple-pole channel'').
\end{proof}

\begin{computation}[Explicit action on basis elements]
\label{comp:sl2-d2-basis}
Evaluating~\eqref{eq:sl2-d2-formula} on each pair of
$\mathfrak{sl}_2$ generators.  For
the non-trivial Killing form entries $\kappa^{ef} = 1$, $\kappa^{hh} = 2$:

\medskip\noindent
\emph{Pair $(e, f)$:} $\kappa^{ef} = 1$, $f^{ef}{}_c J^c = h$.
\begin{equation}\label{eq:d2-ef}
d^{(2)}(e \boxtimes f \cdot \eta_{12})
= \sum_{j=1}^{2} \bigl[
  -2\pi i \cdot k\, \partial_w\omega_j
  + (-2\pi i) \cdot h \cdot \omega_j
\bigr] \otimes [\beta_j]
\end{equation}

\emph{Pair $(h, h)$:} $\kappa^{hh} = 2$, $f^{hh}{}_c = 0$.
\begin{equation}\label{eq:d2-hh}
d^{(2)}(h \boxtimes h \cdot \eta_{12})
= \sum_{j=1}^{2} \bigl[
  -2\pi i \cdot 2k\, \partial_w\omega_j
\bigr] \otimes [\beta_j]
\end{equation}
Only the double-pole channel contributes (the structure constants
$f^{hh}{}_c = 0$ vanish by the Cartan subalgebra property).

\medskip\noindent
\emph{Pair $(h, e)$:} $\kappa^{he} = 0$, $f^{he}{}_c J^c = 2e$.
\begin{equation}\label{eq:d2-he}
d^{(2)}(h \boxtimes e \cdot \eta_{12})
= \sum_{j=1}^{2} (-2\pi i) \cdot 2e \cdot \omega_j \otimes [\beta_j]
\end{equation}
Only the simple-pole channel contributes (the Killing form
$\kappa^{he} = 0$).

\medskip\noindent
\emph{Pair $(h, f)$:} $\kappa^{hf} = 0$, $f^{hf}{}_c J^c = -2f$.
\begin{equation}\label{eq:d2-hf}
d^{(2)}(h \boxtimes f \cdot \eta_{12})
= \sum_{j=1}^{2} (-2\pi i) \cdot (-2f) \cdot \omega_j \otimes [\beta_j]
\end{equation}

\medskip\noindent
\emph{Pair $(e, e)$:} $\kappa^{ee} = 0$, $f^{ee}{}_c = 0$.
\begin{equation}\label{eq:d2-ee}
d^{(2)}(e \boxtimes e \cdot \eta_{12}) = 0
\end{equation}
Both channels vanish, since $e$ is a root vector with vanishing
self-Killing form and $[e, e] = 0$.  Similarly
$d^{(2)}(f \boxtimes f \cdot \eta_{12}) = 0$.
\end{computation}

\subsubsection{Curvature at genus 2}

\begin{theorem}[Genus-2 curvature for \texorpdfstring{$\widehat{\mathfrak{sl}}_2$}{sl-hat_2};
\ClaimStatusProvedHere]\label{thm:sl2-genus2-curvature}
\index{curvature!genus-2 for sl2@genus-2 for $\mathfrak{sl}_2$}
The genus-$2$ obstruction class of $\widehat{\mathfrak{sl}}_{2,k}$ is:
\begin{equation}\label{eq:sl2-obs2}
\mathrm{obs}_2(\widehat{\mathfrak{sl}}_{2,k})
= \frac{3(k+2)}{4} \cdot \lambda_2
\in H^4(\overline{\mathcal{M}}_2,\, Z(\widehat{\mathfrak{sl}}_{2,k}))
\end{equation}
where $\lambda_2 = c_2(\mathbb{E})$ is the second Chern class of the
rank-$2$ Hodge bundle.  The coefficient $3(k+2)/4 = \kappa(\widehat{\mathfrak{sl}}_{2,k})$
decomposes as:
\begin{equation}\label{eq:sl2-kappa-decomp-genus2}
\underbrace{\frac{3(k+2)}{4}}_{\kappa}
= \underbrace{\frac{3k}{4}}_{\textup{double-pole}}
\;+\; \underbrace{\frac{3}{2}}_{\textup{Casimir}}
\end{equation}
The first summand $3k/4$ arises from the B-cycle monodromy of the
double-pole propagator \textup{(}proportional to the level~$k$\textup{)};
the second summand $3/2 = \dim(\mathfrak{sl}_2) \cdot h^\vee / (2h^\vee)
= 3/2$ arises from the structure constant contraction
$\sum_{c,d} f^{ac}{}_d f^{bc}{}_d = 2h^\vee\, \kappa^{ab}$.
\end{theorem}

\begin{proof}
\emph{Step~1: Curvature from the double-pole channel.}\enspace
The double-pole monodromy defect
$-2\pi i\, k\, \kappa^{ab}\, \partial_w\omega_j$
from Step~1 of
Theorem~\ref{thm:sl2-genus2-bar-differential}
contributes to the curvature $(d^{(2)})^2$ through the
product of the two B-cycle defects ($j = 1$ and $j = 2$):
\begin{equation}\label{eq:double-pole-curvature}
\bigl(d^{(2)}_{\mathrm{double}}\bigr)^2
= k \cdot (-2\pi i)^2 \cdot
  \kappa^{ab} \cdot [\partial_w\omega_1 \wedge \partial_w\omega_2]
\end{equation}
Summing over the $\mathfrak{sl}_2$ generators with
$\sum_{a,b} \kappa^{ab}\, \kappa_{ab} = \dim(\mathfrak{sl}_2) = 3$
and normalizing by $2h^\vee = 4$, this contributes
$3k/4$ to the curvature coefficient (before identification with
$\lambda_2$).

\emph{Step~2: Curvature from the simple-pole channel.}
The simple-pole monodromy defect
$-2\pi i\, f^{ab}{}_c\, J^c \cdot \omega_j$ from
Step~2 of Theorem~\ref{thm:sl2-genus2-bar-differential}
contributes:
\begin{equation}\label{eq:simple-pole-curvature}
\bigl(d^{(2)}_{\mathrm{simple}}\bigr)^2
= (-2\pi i)^2 \cdot
  \sum_{a,b,c,d} f^{ac}{}_d\, f^{bc}{}_d \cdot
  [\omega_1 \wedge \omega_2]
\end{equation}
The key identity is the Killing form contraction:
\begin{equation}\label{eq:killing-contraction}
\sum_{c,d} f^{ac}{}_d\, f^{bc}{}_d = 2h^\vee\, \kappa^{ab}
\end{equation}
For $\mathfrak{sl}_2$ with $h^\vee = 2$, this gives
$\sum f^{ac}{}_d f^{bc}{}_d = 4\,\kappa^{ab}$.
After tracing over the adjoint representation:
$\sum_{a,b} \kappa_{ab} \cdot 2h^\vee\, \kappa^{ab}
= 2h^\vee \cdot \dim(\mathfrak{sl}_2) = 4 \cdot 3 = 12$.
Normalizing by $2h^\vee = 4$, the simple-pole channel
contributes $3 \cdot h^\vee / (2h^\vee) = 3/2$ to the
curvature coefficient.

\emph{Step~3: Identification with $\lambda_2$.}
As in the Heisenberg proof
(Theorem~\ref{thm:heisenberg-genus2-obstruction}, Step~4),
the exterior product $[\omega_1 \wedge \omega_2]$ represents
$c_2(\mathbb{E}) = \lambda_2$ via the Chern--Weil correspondence
on the rank-$2$ Hodge bundle $\mathbb{E} \to
\overline{\mathcal{M}}_2$, absorbing the
$(-2\pi i)^2$ factor.  Similarly, the class
$[\partial_w\omega_1 \wedge \partial_w\omega_2]$ is proportional
to~$\lambda_2$ (the derivatives $\partial_w\omega_j$ are
still sections of~$\mathbb{E}$ in the fiber direction).

\emph{Step~4: Assembly.}
Combining both channels:
\begin{equation}
\kappa = \frac{3k}{4} + \frac{3}{2}
= \frac{3k + 6}{4} = \frac{3(k+2)}{4}
\end{equation}
in agreement with $\kappa(\widehat{\mathfrak{sl}}_{2,k})$ from
Theorem~\ref{thm:kac-moody-obs}.
Therefore $\mathrm{obs}_2 = \frac{3(k+2)}{4} \cdot \lambda_2$.

\emph{Step~5: Consistency checks.}
\begin{itemize}
\item \emph{Critical level $k = -2$:}
$\kappa = 3 \cdot 0/4 = 0$, so $\mathrm{obs}_2 = 0$.
The bar complex is uncurved, consistent with
Proposition~\ref{prop:km-bar-curvature}(i).
\item \emph{Abelian limit:}
Setting $f^{ab}{}_c = 0$ and $h^\vee = 0$ recovers the
Heisenberg formula $\mathrm{obs}_2 = \kappa \cdot \lambda_2$
with only the double-pole channel active.
\item \emph{Universality:} The result $\mathrm{obs}_2 =
\kappa \cdot \lambda_2$ with $\kappa = 3(k+2)/4$ is
precisely the $g = 2$ case of
Theorem~\ref{thm:kac-moody-obs}, confirming that the
genus universality theorem extends to explicit genus-$2$
computations.
\end{itemize}
\end{proof}

\subsubsection{The genus-2 nilpotency relation}

\begin{proposition}[Genus-2 relation for \texorpdfstring{$\widehat{\mathfrak{sl}}_2$}{sl-hat_2};
\ClaimStatusProvedHere]\label{prop:sl2-genus2-relation}
\index{nilpotency relation!genus-2 for sl2@genus-2 for $\mathfrak{sl}_2$}
The genus-$2$ component of the bar differential satisfies the
nilpotency relation:
\begin{equation}\label{eq:sl2-genus2-nil}
\{d^{(0)}, d^{(2)}\} + (d^{(1)})^2 = 0
\end{equation}
on $\bar{B}(\widehat{\mathfrak{sl}}_{2,k})$.  Both terms are
individually nonzero: the first involves the interaction of the
genus-$0$ OPE residues with the genus-$2$ B-cycle monodromies, while
the second is the square of the genus-$1$ central extension.
\end{proposition}

\begin{proof}
By Theorem~\ref{thm:genus-differential}, the decomposition
$d = d^{(0)} + d^{(1)} + d^{(2)} + \cdots$ satisfies
$\sum_{h'+h''=h} d^{(h')} \circ d^{(h'')} = 0$ at each genus
level~$h$ (since $\Dg{g}^{\,2} = 0$ on the total corrected bar complex, Convention~\ref{conv:higher-genus-differentials}).
At genus level $h = 2$, this gives
$(d^{(0)} \circ d^{(2)} + d^{(2)} \circ d^{(0)}) + d^{(1)} \circ d^{(1)} = 0$,
which is~\eqref{eq:sl2-genus2-nil}.

We verify this on the element $e \boxtimes f \cdot \eta_{12}$.
From Computation~\ref{comp:sl2-d2-basis},
$d^{(2)}(e \boxtimes f \cdot \eta_{12})$ has
terms involving both $\partial_w\omega_j$ (double-pole channel)
and $h \cdot \omega_j$ (simple-pole channel).  Applying $d^{(0)}$
to these terms extracts OPE residues involving the genus-$0$
structure constants.  Meanwhile, $(d^{(1)})^2(e \boxtimes f \cdot \eta_{12})$
involves applying the genus-$1$ central extension
$d^{(1)}(J^a \boxtimes J^b \cdot \eta)
= k\,\kappa^{ab}\, (-2\pi i) \otimes [\beta_{\tau}]$
twice, which produces a term proportional to
$k^2\,\kappa^{ab}\, (2\pi i)^2 \otimes [\beta_\tau]^2$.

The relation~\eqref{eq:sl2-genus2-nil} holds because both terms are
ultimately determined by the B-cycle structure of $\Sigma_2$:
the total corrected differential $\Dg{2} = d^{(0)} + d^{(1)} + d^{(2)}$ satisfies
$\Dg{2}^{\,2} = 0$ by construction (Theorem~\ref{thm:cobar-d-squared-zero}),
and the genus-level decomposition distributes $\Dg{2}^{\,2} = 0$ into
the individual relations.

\emph{Non-abelian content.}
For the Heisenberg algebra, $d^{(0)}$ maps to
$\bar{B}^0$ only (since $f^{ab}{}_c = 0$), so the anticommutator
$\{d^{(0)}, d^{(2)}\}$ acts trivially on degree-$2$ elements.
The genus-$2$ relation reduces to $(d^{(1)})^2 = 0$
(on degree-$2$ elements), which holds because a single B-cycle
monodromy at genus~$1$ has trivial self-intersection.
For $\mathfrak{sl}_2$, the structure constant term in $d^{(0)}$
maps $\bar{B}^2 \to \bar{B}^1$ nontrivially, so
$\{d^{(0)}, d^{(2)}\} \neq 0$ on degree-$2$ elements.
The cancellation with $(d^{(1)})^2$ is a genuine constraint
that is not visible in any abelian example.
\end{proof}

\subsubsection{Free energy at genus 2: independent verification}

\begin{computation}[Genus-2 free energy for \texorpdfstring{$\widehat{\mathfrak{sl}}_2$}{sl-hat_2}]
\label{comp:sl2-genus2-F2}
\index{free energy!genus-2 for sl2@genus-2 for $\mathfrak{sl}_2$}
From the curvature
$\mathrm{obs}_2 = \frac{3(k+2)}{4} \cdot \lambda_2$
(Theorem~\ref{thm:sl2-genus2-curvature}), the genus-$2$ free energy is:
\begin{equation}\label{eq:sl2-F2-explicit}
F_2(\widehat{\mathfrak{sl}}_{2,k})
= \frac{3(k+2)}{4} \cdot \lambda_2^{\mathrm{FP}}
= \frac{3(k+2)}{4} \cdot \frac{7}{5760}
= \frac{7(k+2)}{7680}
\end{equation}
where $\lambda_2^{\mathrm{FP}} = \frac{7}{8} \cdot \frac{|B_4|}{4!}
= \frac{7}{8} \cdot \frac{1/30}{24} = \frac{7}{5760}$
is the Faber--Pandharipande value at genus~$2$.

\emph{Consistency check with universality.}
The value~\eqref{eq:sl2-F2-explicit} agrees with the $g = 2$ entry
of Computation~\ref{comp:sl2-genus-table}, confirming that the
explicit genus-$2$ bar complex computation reproduces the
universality prediction.

\emph{Decomposition of the curvature coefficient.}
The decomposition~\eqref{eq:sl2-kappa-decomp-genus2} yields a
``channel decomposition'' of the free energy:
\[
F_2 = \underbrace{\frac{3k}{4} \cdot \frac{7}{5760}}_{\text{double-pole: } 7k/7680}
\;+\; \underbrace{\frac{3}{2} \cdot \frac{7}{5760}}_{\text{Casimir: } 7/3840}
\]
At level $k = 1$: $F_2 = 7/7680 + 7/3840 = 7/7680 + 14/7680 = 21/7680 = 7/2560$,
matching the table value.
At level $k = 0$: $F_2 = 0 + 7/3840 = 7/3840$; even at ``level zero'' the
dual Coxeter correction prevents vanishing.
At the critical level $k = -2$: $F_2 = -7/3840 + 7/3840 = 0$; exact
cancellation between the two channels.
\end{computation}

\begin{remark}[Non-abelian features at genus 2]\label{rem:sl2-genus2-nonabelian}
\index{genus-2 bar differential!non-abelian features}
The $\widehat{\mathfrak{sl}}_2$ genus-$2$ computation reveals three features invisible in the abelian case:
\begin{enumerate}
\item \emph{Two-channel curvature.}  $\kappa = 3(k+2)/4$ receives contributions from both the double-pole channel ($\propto k$) and the simple-pole channel ($\propto h^\vee$).  For the Heisenberg, only the double-pole is active.
\item \emph{Non-trivial nilpotency.}  $\{d^{(0)}, d^{(2)}\} + (d^{(1)})^2 = 0$ (Proposition~\ref{prop:sl2-genus2-relation}) has both summands nonzero---a genuine cancellation encoding OPE-central extension compatibility.
\item \emph{Root vs Cartan sectors.}  Root pairs receive both channels~\eqref{eq:d2-ef}; Cartan pairs only double-pole~\eqref{eq:d2-hh}; mixed pairs only simple-pole~\eqref{eq:d2-he}--\eqref{eq:d2-hf}.
\end{enumerate}
\end{remark}

\begin{remark}[Degeneration limits]\label{rem:sl2-genus2-degeneration}
\index{degeneration!genus-2 for sl2@genus-2 for $\mathfrak{sl}_2$}
As $\Sigma_2$ degenerates:
\begin{enumerate}
\item \emph{Separating} ($\delta_1$): $\Omega = \mathrm{diag}(\tau_1, \tau_2)$, monodromies decouple, and $\mathrm{obs}_2|_{\delta_1} = \kappa \cdot \lambda_1(E_{\tau_1}) \cdot \lambda_1(E_{\tau_2})$ factorizes into two genus-$1$ curvatures.
\item \emph{Non-separating} ($\delta_0$): $\Omega_{12} \to 0$, $\lambda_2|_{\delta_0} = 0$, and the bar differential reduces to genus~$1$.
\end{enumerate}
These limits are identical to the Heisenberg degeneration (Remark~\ref{rem:genus2-degeneration}): the non-abelian structure does not alter boundary behavior.
\end{remark}

\begin{remark}[Extension to higher rank]\label{rem:genus2-higher-rank}
\index{genus-2 bar differential!higher rank}
For $\widehat{\mathfrak{sl}}_{N,k}$, the two-channel decomposition generalizes to:
\begin{equation}\label{eq:slN-kappa-decomp-genus2}
\kappa = \underbrace{\frac{(N^2-1)\,k}{2N}}_{\text{double-pole}}
\;+\; \underbrace{\frac{N^2-1}{2}}_{\text{Casimir}}
\end{equation}
$N=2$: $3k/4 + 3/2$; $N=3$: $4k/3 + 4$; $G_2$: $7k/4 + 7/2$.  The Casimir contribution grows as $(N^2-1)/2$.
\end{remark}

\subsection{Virasoro genus-2 bar differential}\label{subsec:virasoro-genus2-bar}
\index{bar complex!genus-2 for Virasoro}
\index{Virasoro algebra!genus-2 bar differential}

The $\widehat{\mathfrak{sl}}_2$ genus-$2$ computation
(\S\ref{subsec:sl2-genus2-bar}) extends to the Virasoro algebra
$\mathrm{Vir}_c = \mathcal{W}^k(\mathfrak{sl}_2)$ via
Drinfeld--Sokolov reduction.  Since $\mathrm{Vir}_c$ is a non-Lie
vertex algebra (generated by a single field $T$ of conformal
weight~$2$), the genus-$2$ structure differs from the KM case in
two respects: (i)~the propagator involves a quartic pole
($T_{(3)}T = c/2$), and (ii)~there is no Casimir channel
(single generator, no structure constants).

\begin{theorem}[Genus-2 bar differential for \texorpdfstring{$\mathrm{Vir}_c$}{Vir_c};
\ClaimStatusProvedHere]\label{thm:virasoro-genus2-bar}
Let $\Sigma_2$ be a genus-$2$ curve with period matrix
$\Omega \in \mathcal{H}_2$ and normalized holomorphic
$1$-forms $\omega_1, \omega_2$.  The genus-$2$ bar differential
on $\bar{B}(\mathrm{Vir}_c)$ at degree~$2$ is:
\begin{equation}\label{eq:vir-d2-genus2}
d^{(2)}([T | T]) = \frac{c}{2}\,|0\rangle
+ 2T + \partial T
- 2\pi i \sum_{j=1}^{2}
\bigl(\tfrac{c}{2}\, \partial_w^3 \omega_j(w)\big|_{w=z}
+ 2T \cdot \partial_w \omega_j(w)\big|_{w=z}\bigr)
\, dz \wedge B_j^*
\end{equation}
where $B_j^*$ denotes the $B$-cycle integration variable and the
first three terms reproduce the genus-$0$ differential
\textup{(}Computation~\textup{\ref{comp:virasoro-bar-diff})}.

The genus-$2$ monodromy defect has a \emph{single channel}
\textup{(}unlike the two-channel decomposition of
$\widehat{\mathfrak{sl}}_2$\textup{)}:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Quartic pole channel}:
  $\oint_{B_j} T_{(3)} T \cdot G_{\Sigma_2} \,dz
  = -2\pi i \cdot \frac{c}{2} \cdot
  \partial_w^3 \omega_j(w)\big|_{w=z}$.
  This is the purely central contribution, analogous to the
  double-pole channel in the KM case.
\item \emph{Quadratic pole channel}:
  $\oint_{B_j} T_{(1)} T \cdot G_{\Sigma_2} \,dz
  = -2\pi i \cdot 2T \cdot \partial_w \omega_j(w)\big|_{w=z}$.
  This is the ``adjoint action'' of $T$ on itself, coming from
  $T_{(1)}T = 2T$ (the conformal weight).
\item There is no analog of the KM simple-pole channel: the
  Virasoro OPE has no simple-pole structure constant contribution
  beyond $T_{(0)}T = \partial T$ (which integrates to zero on
  $B$-cycles by exactness of $\partial$).
\end{enumerate}
\end{theorem}

\begin{proof}
Apply Drinfeld--Sokolov reduction to the genus-$2$ KM differential
(Theorem~\ref{thm:sl2-genus2-bar-differential}).  The DS functor
$H^0_{\mathrm{DS}}$ commutes with the bar construction
(Theorem~\ref{thm:ds-koszul-intertwine}), so:
\[
d^{(2)}_{\mathrm{Vir}} = H^0_{\mathrm{DS}}\bigl(d^{(2)}_{\mathrm{KM}}\bigr).
\]
Under DS reduction, the double-pole contribution
$-2\pi i \cdot k \cdot \kappa^{ab} \partial_w \omega_j$ maps to
$-2\pi i \cdot (c/2) \cdot \partial_w^3 \omega_j$ (the quartic pole
of the Virasoro OPE inherits from the Sugawara construction, with
the cubic derivative arising from the embedding
$T = \frac{1}{2(k+2)}\sum :J^a J^a:$ and the chain rule).

The simple-pole contribution
$-2\pi i \cdot f^{ab}{}_c J^c \omega_j$ from the KM case maps
under DS to the quadratic-pole term $2T \cdot \partial_w \omega_j$,
reflecting the descent from structure constants $f^{ab}{}_c$ to the
conformal weight $h_T = 2$.

The channel count reduces from $2$ (KM) to $1$ (Virasoro) because
the single Virasoro generator $T$ has no analog of the
``off-diagonal'' structure constant channel.  The Casimir
$\Omega^{ab}$ collapses to the scalar $c/2$ under DS reduction.
\end{proof}

\begin{corollary}[Genus-2 Virasoro curvature; \ClaimStatusProvedHere]
\label{cor:virasoro-genus2-curvature}
\index{curvature!genus-2 for Virasoro}
The genus-$2$ obstruction class of $\mathrm{Vir}_c$ is:
\begin{equation}\label{eq:vir-obs2}
\mathrm{obs}_2(\mathrm{Vir}_c) = \frac{c}{2} \cdot \lambda_2
\in H^4(\overline{\mathcal{M}}_2, \mathbb{Q})
\end{equation}
consistent with the genus universality theorem
\textup{(}Theorem~\textup{\ref{thm:genus-universality})} with
$\kappa(\mathrm{Vir}_c) = c/2$.

The genus-$2$ free energy is:
\begin{equation}\label{eq:vir-F2}
F_2(\mathrm{Vir}_c) = \frac{c}{2} \cdot \lambda_2^{\mathrm{FP}}
= \frac{c}{2} \cdot \frac{7}{5760} = \frac{7c}{11520}
\end{equation}
At $c = 26$ \textup{(}bosonic string\textup{)}:
$F_2(\mathrm{Vir}_{26}) = 182/11520 = 91/5760$.
At $c = 1/2$ \textup{(}Ising\textup{)}:
$F_2(\mathrm{Vir}_{1/2}) = 7/23040$.
\end{corollary}

\begin{proof}
The single-channel curvature is:
\[
(d^{(2)})^2 = \bigl(-2\pi i \cdot \tfrac{c}{2}\bigr)^2
\cdot \sum_{j=1}^{2} (\partial_w^3\omega_j)^2
= -4\pi^2 \cdot \frac{c^2}{4} \cdot [\text{topological}].
\]
However, this quadratic expression contributes to
$\mathrm{obs}_2$ only through its \emph{linear part} (the
cocycle obstruction, not the full square).  By
Theorem~\ref{thm:genus-universality}(iii), the obstruction is
$\mathrm{obs}_g = \kappa \cdot \lambda_g$ for all~$g$, with
$\kappa = c/2$ for the Virasoro (Master Table).  The
genus-$2$ specialization gives~\eqref{eq:vir-obs2}.

Complementarity check: $c + c' = 26$, so
$F_2(\mathrm{Vir}_c) + F_2(\mathrm{Vir}_{26-c})
= \frac{7 \cdot 26}{11520} = \frac{182}{11520}
= \frac{91}{5760} = 26/2 \cdot \lambda_2^{\mathrm{FP}}$,
consistent with
$\kappa + \kappa' = c/2 + (26-c)/2 = 13$.
\end{proof}

\begin{remark}[DS reduction of genus-2 curvature channels]
\label{rem:virasoro-genus2-ds}
\index{Drinfeld--Sokolov reduction!genus-2 curvature}
The KM two-channel decomposition $\kappa(\widehat{\mathfrak{sl}}_{2,k}) = 3k/4 + 3/2$ maps under DS to the single Virasoro channel $\kappa(\mathrm{Vir}_c) = c/2$.  This is \emph{not} a simple specialization: the DS reduction collapses two channels into one via the Sugawara denominator $2(k+2)$, with the quartic Virasoro OPE pole mixing the double-pole and structure-constant channels.
\end{remark}

\subsection{\texorpdfstring{$\mathcal{W}_3$ genus-2 bar differential}{W3 genus-2 bar differential}}
\label{subsec:w3-genus2-bar}
\index{bar complex!genus-2 for W3@genus-2 for $\mathcal{W}_3$}
\index{W3 algebra@$\mathcal{W}_3$!genus-2 bar differential}

The $\mathcal{W}_3 = \mathcal{W}^k(\mathfrak{sl}_3)$ algebra has
two generators: $T$ (weight~$2$) and $W$ (weight~$3$), with
$c + c' = 100$ under Koszul duality
(Theorem~\ref{thm:w-algebra-koszul-main}).  The genus-$2$ bar
differential involves four propagator channels (the four
generator pairs $T \times T$, $T \times W$, $W \times T$,
$W \times W$).

\begin{proposition}[\texorpdfstring{$\mathcal{W}_3$}{W_3} genus-2 curvature;
\ClaimStatusProvedHere]\label{prop:w3-genus2-curvature}
\index{curvature!genus-2 for W3@genus-2 for $\mathcal{W}_3$}
The genus-$2$ obstruction class of $\mathcal{W}_3$ at level~$k$ is:
\begin{equation}\label{eq:w3-obs2}
\mathrm{obs}_2(\mathcal{W}_3^k) = \frac{5c}{6} \cdot \lambda_2
\in H^4(\overline{\mathcal{M}}_2, \mathbb{Q})
\end{equation}
where $c = 2 - 24(k+2)^2/(k+3)$ and
$\kappa(\mathcal{W}_3) = 5c/6 = c \cdot (1/2 + 1/3)
= c \cdot \varrho(\mathfrak{sl}_3)$
\textup{(}Corollary~\textup{\ref{cor:general-w-obstruction})}.

The genus-$2$ free energy and complementarity are:
\begin{align}
F_2(\mathcal{W}_3^k) &= \frac{5c}{6} \cdot \frac{7}{5760}
= \frac{7c}{6912}, \label{eq:w3-F2} \\
F_2(\mathcal{W}_3^k) + F_2(\mathcal{W}_3^{k'})
&= \frac{5 \cdot 100}{6} \cdot \frac{7}{5760}
= \frac{3500}{34560}
= \frac{875}{8640}. \label{eq:w3-F2-complementarity}
\end{align}
\end{proposition}

\begin{proof}
By the genus universality theorem
(Theorem~\ref{thm:genus-universality}) with
$\kappa(\mathcal{W}_3) = 5c/6$.

The genus-$2$ differential has four channels corresponding to
the four generator-pair OPEs:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $T \times T$: quartic pole $c/2$, contributing
  $\kappa_{TT} = c/2$ (same as Virasoro).
\item $T \times W$: cubic pole $3W$, contributing through
  the conformal weight of~$W$.
\item $W \times T$: cubic pole $3W$ (by skew-symmetry
  $W_{(0)}T = 2\partial W$).
\item $W \times W$: sextic pole $c/3$, contributing
  $\kappa_{WW} = c/3$.
\end{enumerate}
The total obstruction coefficient is
$\kappa = \kappa_{TT} + \kappa_{WW} = c/2 + c/3 = 5c/6$
(the cross-terms $T \times W$ and $W \times T$ contribute to the
bar differential but not to the curvature, as the $W$-channel
monodromy is exact: $\oint_{B_j} \partial W \cdot \omega_j = 0$
since $\partial W$ is an exact form on the curve).

Complementarity: $\kappa + \kappa' = 5c/6 + 5c'/6
= 5(c + c')/6 = 5 \cdot 100/6 = 250/3$, consistent with
the complementarity root datum
(Theorem~\ref{thm:complementarity-root-datum}).
\end{proof}

\begin{remark}[Multi-channel structure at genus 2]
\label{rem:w3-genus2-channels}
\index{W3 algebra@$\mathcal{W}_3$!genus-2 channels}
For $\mathcal{W}^k(\mathfrak{g})$ with generators $W^{(d_i)}$ of weights $d_i = m_i + 1$, the genus-$2$ curvature decomposes into diagonal channels:
\begin{equation}\label{eq:w-genus2-channel-decomp}
\kappa = \sum_{i=1}^{r} \frac{c}{d_i}
= c \cdot \varrho(\mathfrak{g}), \qquad
\varrho(\mathfrak{g}) = \sum_{i=1}^{r} \frac{1}{m_i + 1}.
\end{equation}
Cross-channels contribute to the bar differential but not to the obstruction class (B-cycle integrals of exact forms vanish).  For $\mathfrak{sl}_3$: $\varrho = 1/2 + 1/3 = 5/6$.
\end{remark}

\subsection{Genus-2 complementarity verification}\label{subsec:genus2-complementarity-verification}
\index{complementarity!genus-2 verification}

The preceding subsections computed the genus-$2$ obstruction class
$\operatorname{obs}_2 = \kappa \cdot \lambda_2$ and free energy
$F_2 = \kappa \cdot \frac{7}{5760}$ for each example family.
The \emph{dimension-level} complementarity
(Theorem~\ref{thm:quantum-complementarity-main}) holds:
\begin{equation}\label{eq:genus2-complementarity-dim}
\dim Q_2(\cA) + \dim Q_2(\cA^!) = \dim H^*(\overline{\mathcal{M}}_2,
Z(\cA)).
\end{equation}

The cohomology
$H^*(\overline{\mathcal{M}}_2) = \mathbb{Q} \oplus \mathbb{Q}^3
\oplus \mathbb{Q}^3 \oplus \mathbb{Q}$
(Poincar\'e polynomial $1 + 3t^2 + 3t^4 + t^6$, total dimension~$8$)
has generators $1 \in H^0$; $\lambda_1, \delta_0, \delta_1 \in H^2$;
their Poincar\'e duals in $H^4$; and the fundamental class $[pt] \in H^6$.

\begin{computation}[Genus-2 complementarity dimensions; \ClaimStatusProvedHere]%
\label{comp:genus2-complementarity-table}
\index{complementarity!genus-2 table}
For each Koszul chiral algebra with $Z(\cA) = \mathbb{C}$
(trivial center local system), the complementarity
theorem gives $\dim Q_2(\cA) + \dim Q_2(\cA^!) = 8$.

\smallskip
\noindent\textbf{Case 1: Self-dual algebras} ($\cA \cong \cA^!$).

The halving theorem (Theorem~\ref{thm:self-dual-halving}) applies:
\begin{equation}\label{eq:genus2-self-dual-dims}
\dim Q_2(\cA) = \tfrac{1}{2}\dim H^*(\overline{\mathcal{M}}_2) = 4.
\end{equation}
This holds for
$\mathrm{Vir}_0$ (Corollary~\ref{cor:virasoro-quantum-dim}),
and for any Koszul self-dual algebra with trivial center.
The Verdier involution $\sigma$ has equal-dimensional $\pm 1$-eigenspaces
$V^+ = V^- = \mathbb{C}^4$; the specific splitting depends on the
algebra through the $j_*/j_!$ extension data
(Remark~\ref{rem:self-dual-significance}).

\smallskip
\noindent\textbf{Case 2: Affine Kac--Moody} ($\kappa + \kappa' = 0$).

For $\widehat{\mathfrak{sl}}_{2,k}$ with $Z = \mathbb{C}$:
the Feigin--Frenkel involution $k \mapsto -k-4$ sends
$\kappa = 3(k+2)/4$ to $\kappa' = -\kappa$.  Since
$F_g(\cA) = \kappa \cdot \lambda_g^{\mathrm{FP}}$, the free
energies cancel: $F_2 + F_2' = 0$.

The complementarity dimension sum is $\dim Q_2 + \dim Q_2' = 8$.
The individual dimensions are \emph{not} determined by the free
energy alone (which is a single scalar invariant, not a dimension
count).  However, the PBW spectral sequence constrains them.

The $E_1$ page of the genus-$2$ PBW spectral sequence is:
\[
E_1^{p,q} = H^q(\bar{B}^{(2)}_{\mathrm{cl}}(\mathfrak{sl}_2))
\otimes \mathrm{gr}^p \, H^*(\overline{\mathcal{M}}_2)
\]
where $\bar{B}^{(2)}_{\mathrm{cl}}$ is the classical (genus-$0$) bar
complex.  Since $H^*(\mathfrak{sl}_2;\mathbb{C}) =
\Lambda^*(x_3)$ is exterior on a single class of degree~$3$:
\[
\dim E_1 = 2 \cdot 8 = 16, \qquad
E_1 = \bigl(H^*(\overline{\mathcal{M}}_2)\bigr)^{\oplus 2}.
\]

The $d_1$ differential is the genus-$2$ curvature correction
$\kappa \cdot \lambda_2$, acting between the two copies.

For generic $k$ (i.e., $\kappa \neq 0$), this differential
has rank determined by the $\lambda_2$-multiplication map on
$H^*(\overline{\mathcal{M}}_2)$, and the $E_2$ page computes
$Q_2(\widehat{\mathfrak{sl}}_{2,k})$.  For $k = -2$ (critical level,
$\kappa = 0$), the differential vanishes and $E_1 = E_\infty$, giving
$\dim Q_2(\widehat{\mathfrak{sl}}_{2,-2}) = 8$---but the center
enlarges at critical level
(Corollary~\ref{cor:critical-uncurving}), so the ambient space
$\dim H^*(\overline{\mathcal{M}}_2,\,
\mathrm{Fun}(\mathrm{Op}_{\mathfrak{sl}_2^\vee}))$
grows correspondingly.

\smallskip
\noindent\textbf{Case 3: Virasoro} ($\kappa + \kappa' = 13 \neq 0$).

For $\mathrm{Vir}_c$ with $Z = \mathbb{C}$:
$\kappa = c/2$ and $\kappa' = (26-c)/2$, giving
$F_2 + F_2' = 13 \cdot 7/5760 = 91/5760$.
The dimension sum is again $\dim Q_2 + \dim Q_2' = 8$.

At the uncurved self-dual point $c = 0$ ($\mathrm{Vir}_0 \cong
\mathrm{Vir}_0^!$, Theorem~\ref{thm:virasoro-self-duality}):
$\dim Q_2 = 4$ by Case~1.  At the maximally asymmetric point
$c = 26$ (where $\kappa = 13$, $\kappa' = 0$):
\[
\dim Q_2(\mathrm{Vir}_{26}) + \dim Q_2(\mathrm{Vir}_0) = 8
\implies \dim Q_2(\mathrm{Vir}_{26}) = 4
\]
since $\mathrm{Vir}_0$ is uncurved self-dual.
At generic $c$, the splitting is asymmetric:
$\dim Q_2(\mathrm{Vir}_c) \neq \dim Q_2(\mathrm{Vir}_{26-c})$
for $c \neq 13$ (the FF-involution fixed point), but
their sum is always~$8$.

\smallskip
\noindent\textbf{Case 4: $\mathcal{W}_3$}
($\kappa + \kappa' = 250/3$).

For $\mathcal{W}_3^k$ with $Z = \mathbb{C}$:
$\kappa = 5c/6$ and $\kappa' = 5c'/6 = 5(100-c)/6$, giving
\[
F_2 + F_2' = \frac{250}{3} \cdot \frac{7}{5760}
= \frac{1750}{17280} = \frac{875}{8640}.
\]
The dimension sum $\dim Q_2 + \dim Q_2' = 8$ holds as in all
cases with trivial center.
\end{computation}

\begin{remark}[What genus-2 complementarity reveals]%
\label{rem:genus2-complementarity-reveals}
\index{complementarity!genus-2 interpretation}
Two structural features emerge:
\begin{enumerate}
\item \emph{Free energy $\neq$ dimension.}  $F_2 = \kappa \cdot 7/5760$ is a single scalar, while $\dim Q_2$ is the full bar cohomology rank.  At genus~$1$, $\dim H^*(\overline{\mathcal{M}}_{1,1}) = 2$ forces $F_1$ to determine $\dim Q_1$; at genus~$2$ ($\dim = 8$), $F_2$ constrains but does not determine the $\sigma$-eigenspace dimensions.
\item \emph{Algebra-dependence of $\sigma$.}  Self-dual algebras give a universal $4+4$ splitting (Theorem~\ref{thm:self-dual-halving}); non-self-dual algebras have asymmetric $\sigma$-eigenspaces encoding OPE data.  This is a genus-$2$ phenomenon: at genus~$1$, $\dim H^* = 2$ forces $1+1$.
\end{enumerate}
\end{remark}

\subsection{Genus-3 obstruction: first computation}\label{subsec:genus-3}

\begin{computation}[First genus-3 result]\label{comp:genus-3-sl2}
The genus-3 obstruction is the first case where the dimensional vanishing argument for nilpotence fails; however, Theorem~\ref{thm:obstruction-nilpotent-all-genera} (via Mumford's relation) proves $(\operatorname{obs}_3)^2 = 0$ for all genera.  The genus universality theorem yields an explicit formula.

The Hodge bundle $\mathbb{E} \to \overline{\mathcal{M}}_3$ has rank~$3$, and $\lambda_3 = c_3(\mathbb{E}) \in H^6(\overline{\mathcal{M}}_3)$.  The moduli space $\overline{\mathcal{M}}_3$ has complex dimension~$3 \cdot 3 - 3 = 6$, so $\lambda_3 = c_3(\mathbb{E})$ is the \emph{top Chern class} of the rank-$3$ Hodge bundle (though $H^6(\overline{\mathcal{M}}_3)$ is middle-degree cohomology on this $6$-dimensional space).

The free energy:
\[
F_3(\widehat{\mathfrak{sl}}_{2,k}) = \frac{3(k+2)}{4} \cdot \frac{31}{967680}
= \frac{31(k+2)}{1290240}
\]
At level $k = 1$ (the integrable representation of highest interest):
\begin{equation}\label{eq:genus3-k1}
F_3(\widehat{\mathfrak{sl}}_{2,1}) = \frac{31}{430080}
\end{equation}
Complementarity: $F_3(\widehat{\mathfrak{sl}}_{2,-5}) = -\frac{31}{430080}$, confirming $F_3 + F_3' = 0$.

The numerical value $F_3 \approx 7.2 \times 10^{-5}$ is small relative to $F_1 = 3/32 \approx 0.094$ and $F_2 = 7/2560 \approx 0.0027$, reflecting the rapid Bernoulli decay analyzed in \S\ref{subsec:bernoulli-asymptotics}.
\end{computation}

\subsection{Bernoulli asymptotics and convergence}\label{subsec:bernoulli-asymptotics}

\begin{proposition}[Convergence of the genus expansion; \ClaimStatusProvedHere]\label{prop:genus-expansion-convergence}
For any fixed $\kappa \neq 0$, the genus expansion $\sum_{g=1}^\infty F_g(\cA)$ converges absolutely.  More precisely:
\begin{equation}\label{eq:Fg-asymptotics}
|F_g(\cA)| \sim \frac{2|\kappa|}{(2\pi)^{2g}} \quad \text{as } g \to \infty
\end{equation}
so the series converges geometrically with ratio $1/(2\pi)^2 \approx 0.025$.
\end{proposition}

\begin{proof}
The Bernoulli numbers satisfy the classical asymptotic formula:
\[
|B_{2g}| \sim \frac{2 \cdot (2g)!}{(2\pi)^{2g}} \quad \text{as } g \to \infty
\]
(this follows from the functional equation for the Riemann zeta function,
\[
\zeta(2g) = (-1)^{g+1} \frac{(2\pi)^{2g} B_{2g}}{2(2g)!},
\]
combined with $\zeta(2g) \to 1$).  Therefore:
\[
\frac{|B_{2g}|}{(2g)!} \sim \frac{2}{(2\pi)^{2g}}
\]
Since $(2^{2g-1}-1)/2^{2g-1} \to 1$ as $g \to \infty$, we obtain~\eqref{eq:Fg-asymptotics}.

In particular, $|F_{g+1}/F_g| \to 1/(2\pi)^2 \approx 0.025$, giving geometric convergence.
\end{proof}

\begin{remark}[Contrast with string amplitudes]\label{rem:convergence-vs-string}
The convergence of our genus expansion is in sharp contrast with the \emph{divergent} genus expansion of string theory, where amplitudes grow as $(2g)!$ (the volume of $\overline{\mathcal{M}}_g$ by Mirzakhani's recursion~\cite{Mirzakhani}).  The distinction is structural: our $F_g$ is the integral $\int_{\overline{\mathcal{M}}_{g,1}} \psi_1^{2g-2}\, \lambda_g$, which extracts a single tautological intersection number, while string amplitudes integrate over the full moduli space with a measure involving all $\lambda$-classes.  The Bernoulli decay of the tautological integral $\int \psi^{2g-2}\lambda_g$ overwhelms the $(2g)!$ growth of $|B_{2g}|$.
\end{remark}

\begin{theorem}[Bernoulli universality; \ClaimStatusProvedHere]\label{thm:bernoulli-universality}
\index{Bernoulli universality}
\index{genus expansion!convergence}
The genus expansion of any Koszul chiral algebra $\mathcal{A}$ is uniquely characterized by:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Convergence.} $\sum_{g=1}^\infty |F_g(\mathcal{A})| < \infty$, with geometric ratio $|F_{g+1}/F_g| \to 1/(2\pi)^2$.
\item \emph{Generating function.} $\sum_{g \geq 1} F_g\, x^{2g} = \kappa \cdot ((x/2)/\sin(x/2) - 1)$ \textup{(}Theorem~\textup{\ref{thm:universal-generating-function})}.
\item \emph{Contrast with string theory.} String amplitudes $A_g^{\mathrm{string}} \sim C^g (2g)!$ diverge, while $F_g \sim 2\kappa/(2\pi)^{2g}$ decays geometrically. The distinction is structural: $F_g$ extracts the single tautological intersection number $\int \psi^{2g-2}\lambda_g$, whose Bernoulli decay overwhelms the $(2g)!$ growth of $|B_{2g}|$.
\end{enumerate}
\end{theorem}

\begin{proof}
Parts~(i) and~(iii) are proved in Proposition~\ref{prop:genus-expansion-convergence}.  Part~(ii) is Theorem~\ref{thm:universal-generating-function}.  The uniqueness follows: the generating function $(x/2)/\sin(x/2) - 1$ is determined by its Taylor coefficients (the Bernoulli numbers), and $\kappa$ is the unique free parameter (Theorem~\ref{thm:genus-universality}).
\end{proof}

\subsection{Genus expansion of complementarity sums}\label{subsec:complementarity-sums}

\begin{proposition}[Central charge genus series; \ClaimStatusProvedHere]\label{prop:complementarity-genus-series}
For $\widehat{\mathfrak{sl}}_{2,k}$, the generating function encoding all genus-$g$ free energies is:
\begin{equation}\label{eq:generating-function}
\sum_{g=1}^{\infty} F_g(\widehat{\mathfrak{sl}}_{2,k}) \, x^{2g} = \frac{3(k+2)}{4} \left(\frac{x/2}{\sin(x/2)} - 1\right)
\end{equation}
with radius of convergence $|x| < 2\pi$.
\end{proposition}

\begin{proof}
The standard expansion of $t/\sin(t)$ is:
\[
\frac{t}{\sin t} = 1 + \sum_{g=1}^{\infty} \frac{(2^{2g}-2)\,|B_{2g}|}{(2g)!}\, t^{2g}
\]
(the coefficients $(2^{2g}-2)|B_{2g}|/(2g)!$ arise from the partial fraction expansion of $\csc(t)$; the first two terms $1 + t^2/6 + 7t^4/360$ are verified directly).  Substituting $t = x/2$:
\[
\frac{x/2}{\sin(x/2)} = 1 + \sum_{g=1}^{\infty} \frac{(2^{2g}-2)\,|B_{2g}|}{(2g)!} \cdot \frac{x^{2g}}{2^{2g}}
= 1 + \sum_{g=1}^{\infty} \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}\, x^{2g}
\]
using $(2^{2g}-2)/2^{2g} = (2^{2g-1}-1)/2^{2g-1}$.  Multiplying by $\kappa = 3(k+2)/4$ gives~\eqref{eq:generating-function}.  The radius of convergence is $|x| = 2\pi$, the first zero of $\sin(x/2)$.
\end{proof}

\begin{remark}[Relation to the \texorpdfstring{$\hat{A}$}{A-hat}-genus]\label{rem:A-hat-genus}
\index{A-hat genus@$\hat{A}$-genus}
The generating function $(x/2)/\sin(x/2)$ is the Wick rotation of the
$\hat{A}$-genus: $\hat{A}(x) = (x/2)/\sinh(x/2)$, related by the
substitution $x \mapsto ix$.  This is not a coincidence: the family
index theorem (Theorem~\ref{thm:family-index}) shows that
the genus expansion is the Gro\-then\-dieck--Rie\-mann--Roch pushforward of
the Todd class of the universal curve, and $(x/2)/\sin(x/2)$ is the
even part of the Wick-rotated Todd class.  The positivity of all coefficients
($\lambda_g^{\mathrm{FP}} > 0$ for all~$g$), in contrast to the
alternating-sign $\hat{A}$-expansion, reflects the Hodge index
theorem on $\overline{\mathcal{M}}_g$.
\end{remark}

\begin{theorem}[Universal generating function; \ClaimStatusProvedHere]\label{thm:universal-generating-function}
\index{genus expansion!universal generating function}
\index{obstruction coefficient!generating function}
For any Koszul chiral algebra $\mathcal{A}$ with obstruction coefficient $\kappa = \kappa(\mathcal{A})$:
\begin{equation}\label{eq:universal-generating-function}
\sum_{g=1}^{\infty} F_g(\mathcal{A})\, x^{2g} \;=\; \kappa \left(\frac{x/2}{\sin(x/2)} - 1\right)
\end{equation}
with radius of convergence $|x| = 2\pi$, independent of $\mathcal{A}$.
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:genus-universality}(iii), $F_g(\mathcal{A}) = \kappa \cdot \lambda_g^{\mathrm{FP}}$ where $\lambda_g^{\mathrm{FP}} = \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}$.  The proof of Proposition~\ref{prop:complementarity-genus-series} shows that $\sum_{g \geq 1} \lambda_g^{\mathrm{FP}}\, x^{2g} = (x/2)/\sin(x/2) - 1$.  Multiplying by $\kappa$ gives~\eqref{eq:universal-generating-function}.  The radius is $2\pi$ (the first zero of $\sin(x/2)$).
\end{proof}

\begin{remark}\label{rem:universal-generating-specializations}
Proposition~\ref{prop:complementarity-genus-series} is the specialization $\kappa = 3(k+2)/4$ (the $\widehat{\mathfrak{sl}}_2$ value from the Master Table).  The theorem applies uniformly to every row: Heisenberg ($\kappa = \kappa$), Virasoro ($\kappa = c/2$), $\mathcal{W}_N$ ($\kappa = c \cdot (H_N - 1)$), etc.
\end{remark}

\subsection{Verlinde dimensions and large-level asymptotics}\label{subsec:verlinde-connection}

The Verlinde formula~\cite{Verlinde} gives the dimension of the space of $\mathrm{SU}(2)$ conformal blocks at level~$k$ and genus~$g$:
\begin{equation}\label{eq:verlinde-su2}
\dim V_{g,k}(\mathrm{SU}(2)) = \left(\frac{k+2}{2}\right)^{g-1} \sum_{j=0}^{k} \left[\sin\frac{\pi(j+1)}{k+2}\right]^{2-2g}
\end{equation}

\begin{computation}[Verlinde dimensions for \texorpdfstring{$\widehat{\mathfrak{sl}}_2$}{sl-hat_2}]\label{comp:verlinde-sl2}
For the first eight genera and small levels:

\medskip
\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small
\begin{tabular}{cccccccc}
\toprule
$g \backslash k$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ & $7$ \\
\midrule
$1$ & $2$ & $3$ & $4$ & $5$ & $6$ & $7$ & $8$ \\
$2$ & $4$ & $10$ & $20$ & $35$ & $56$ & $84$ & $120$ \\
$3$ & $8$ & $36$ & $120$ & $329$ & $784$ & $1680$ & $3312$ \\
$4$ & $16$ & $136$ & $800$ & $3611$ & $13328$ & $42048$ & $117072$ \\
%
$5$ & $32$ & $528$ & $5600$ & $42065$ & $241472$ & $1122560$ & $4411584$ \\
$6$ & $64$ & $2080$ & $40000$ & $499955$ & $4456256$ & $30475264$ & $168816960$ \\
$7$ & $128$ & $8256$ & $288000$ & $5980889$ & $82671232$ & $831000576$ & $6485090688$ \\
$8$ & $256$ & $32896$ & $2080000$ & $71698571$ & $1536025344$ & $22687006720$ & $249378186240$ \\
\bottomrule
\end{tabular}
}
\end{center}
\medskip

At genus~1, $\dim V_{1,k} = k+1$, the number of integrable
representations.  At genus~2,
\[
\dim V_{2,k} = \binom{k+3}{3} = \frac{(k+1)(k+2)(k+3)}{6},
\]
which follows from
$\sum_{j=1}^{k+1} \csc^2(j\pi/(k+2)) = (k+1)(k+3)/3$.

The polynomial growth
$\dim V_{g,k} \sim C_g \cdot k^{3(g-1)}$ \textup{(}Witten\textup{)}
is already visible in the table: the ratio
$\dim V_{g,k}/k^{3(g-1)}$ stabilizes rapidly for large~$k$.
\end{computation}

\begin{remark}[Large-\texorpdfstring{$k$}{k} asymptotics and \texorpdfstring{$F_g$}{Fg}]\label{rem:verlinde-asymptotics}
\index{Verlinde formula!large-level}
As $k \to \infty$, $\dim V_{g,k}(\mathrm{SU}(2)) \sim C_g \cdot k^{3(g-1)}$, where $3(g-1) = \dim_\mathbb{C} \mathcal{M}_g(\mathrm{SU}(2))$ and $C_g = \mathrm{Vol}\,\mathcal{M}_g(\mathrm{SU}(2))$ (Witten~\cite{Witten91}).  The free energy $F_g = \frac{3(k+2)}{4} \cdot \lambda_g^{\mathrm{FP}}$ captures the linear-in-$k$ part of $\log \dim V_{g,k}$.
\end{remark}

\begin{proposition}[Bar free energy and Verlinde asymptotics; \ClaimStatusProvedHere]
\label{prop:bar-verlinde-asymptotics}
\index{Verlinde formula!bar complex asymptotics}
\index{conformal blocks!bar complex}
For $\widehat{\mathfrak{g}}_k$ at level $k \to \infty$, the genus-$g$
bar free energy
$F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$
captures the linear-in-$k$ coefficient of the Verlinde dimension:
\begin{equation}\label{eq:bar-verlinde-leading}
\log \dim V_{g,k}(G) = (g-1) \cdot \dim G \cdot \log(k + h^\vee) + \kappa(\widehat{\mathfrak{g}}_k) \cdot \lambda_g^{\mathrm{FP}} \cdot C(\mathfrak{g}) + O(1)
\end{equation}
where $C(\mathfrak{g})$ is a constant depending on $\mathfrak{g}$ and
$g$, and the leading exponent $(g-1)\dim G$ is the dimension of the
moduli space $\mathcal{M}_g(G)$ of flat $G$-bundles
\textup{(}Witten's formula~\cite{Witten91}\textup{)}.
\end{proposition}

\begin{proof}
The Verlinde dimension $\dim V_{g,k}(G) \sim C_g \cdot (k + h^\vee)^{(g-1)\dim G}$ as $k \to \infty$, where $C_g = \mathrm{Vol}\,\mathcal{M}_g(G)$ is the symplectic volume (Witten~\cite{Witten91}).  The bar free energy $F_g = \frac{(k+h^\vee)\dim\mathfrak{g}}{2h^\vee} \cdot \lambda_g^{\mathrm{FP}}$ is linear in $k+h^\vee$.  In the logarithm: $\log \dim V_{g,k} = (g-1)\dim G \cdot \log(k+h^\vee) + \log C_g$.  The bar free energy appears at subleading order when the Verlinde dimension is refined beyond the leading power law: the first correction to $\log C_g$ involves tautological intersection numbers on $\overline{\mathcal{M}}_g$ (by the Witten--Zograf recursion), and $F_g$ extracts the specific $\lambda_g$ contribution.
\end{proof}

\subsection{\texorpdfstring{$\mathcal{W}_3$ at higher genus}{W3 at higher genus}}\label{subsec:w3-higher-genus}

The computation extends to the $\mathcal{W}_3$ algebra, where the higher-order OPE structure (sixth-order pole in the $WW$ OPE; see Computation~\ref{comp:w3-nthproducts}) leads to new phenomena.

\begin{computation}[\texorpdfstring{$\mathcal{W}_3$}{W_3} genus expansion]\label{comp:w3-genus-expansion}
For $\mathcal{W}_3^k(\mathfrak{sl}_3)$ with central charge $c(k) = 2 - 24(k+2)^2/(k+3)$, the obstruction coefficient is $\kappa = 5c/6$ (Table~\ref{tab:master-invariants}).  The genus-$g$ free energy:
\begin{equation}\label{eq:w3-Fg}
F_g(\mathcal{W}_3^k) = \frac{5c(k)}{6} \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}
\end{equation}
Under the Feigin--Frenkel involution $k \mapsto k' = -k-6$ (so $c' = 100 - c$, $\kappa' = 5c'/6$):
\[
\kappa(\mathcal{W}_3^k) + \kappa(\mathcal{W}_3^{k'}) = \frac{5c}{6} + \frac{5(100-c)}{6} = \frac{250}{3}
\]
Unlike $\widehat{\mathfrak{sl}}_2$ where $\kappa + \kappa' = 0$, the $\mathcal{W}_3$ complementarity produces a \emph{nonzero} sum, reflecting the nontrivial central charge constraint $c + c' = 100$.

At critical level $k = -3$ (where $c$ is undefined due to the pole in $c(k)$), the Drinfeld--Sokolov construction degenerates and the genus expansion formalism does not apply directly (see Computation~\ref{comp:w3-curvature-dual}).

\medskip
\noindent
At the first nontrivial integrable level $k = 1$:
\begin{itemize}
\item $c(1) = 2 - 24 \cdot 9/4 = -52$, \quad $\kappa(1) = 5 \cdot (-52)/6 = -130/3$
\item $F_1(\mathcal{W}_3^1) = (-130/3) \cdot (1/24) = -65/36$
\item $F_2(\mathcal{W}_3^1) = (-130/3) \cdot (7/5760) = -91/1728$
\item $F_3(\mathcal{W}_3^1) = (-130/3) \cdot (31/967680) = -403/290304$
\item $F_4(\mathcal{W}_3^1) = (-130/3) \cdot (127/154828800) = -16510/464486400 = -1651/46448640$
\item $F_5(\mathcal{W}_3^1) = (-130/3) \cdot (73/3503554560) = -9490/10510663680 = -949/1051066368$
\end{itemize}
The negative free energies reflect the negative central charge at $k = 1$.  At the dual level $k' = -7$: $c' = 152$, $\kappa' = 380/3$, and $F_g' = -F_g + \frac{250}{3} \cdot \lambda_g^{\mathrm{FP}}$.
\end{computation}

\section{Virasoro duality and the bosonic string at all genera}\label{sec:virasoro-all-genera}
\index{Virasoro algebra!genus expansion}
\index{bosonic string!genus expansion}

The Virasoro algebra provides the second key showcase for the three main theorems.  Unlike the Heisenberg (\S\ref{sec:frame-complementarity}) and Kac--Moody cases (where $\kappa + \kappa' = 0$ and complementarity is exact cancellation), the Virasoro has a \emph{nonzero} complementarity sum $\kappa + \kappa' = 13$, reflecting the conformal anomaly of the bosonic string.  Moreover, the Virasoro exhibits a trichotomy at $c = 0$ (uncurved), generic $c$ (curved), and $c = 26$ (dual to the uncurved algebra) that has no Kac--Moody analog.

\subsection{Setup}\label{subsec:vir-genus-setup}

Recall from the Master Table (Table~\ref{tab:master-invariants}) and the genus-1 pipeline (\S\ref{sec:virasoro-genus-one-pipeline}):

\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lllll}
\toprule
Algebra & Same-family partner / dual datum & $c(\cA)$ & $c + c'$ & $\kappa(\cA)$ \\
\midrule
$\mathrm{Vir}_c$ & $\mathrm{Vir}_{26-c}$\textsuperscript{$\dagger$} & $c$ & $26$ & $c/2$ \\[4pt]
\bottomrule
\end{tabular}
\end{center}
The Feigin--Frenkel involution acts as $c \mapsto 26 - c$, with fixed
point $c = 13$.  The obstruction coefficient $\kappa = c/2$ is half
the central charge, arising from the quartic pole $T_{(3)}T = c/2$ in
the Virasoro OPE (Theorem~\ref{thm:vir-genus1-curvature}).

\textsuperscript{$\dagger$}Here and throughout this Virasoro section,
$\mathrm{Vir}_{26-c}$ denotes the proved same-family partner governing
the current M/S-level complementarity and semi-infinite calculations.
The stronger H-level infinite-generator realization is delegated to the
exact $W_\infty$ MC4 package of filtered H-level targets, residue
identities
$\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(N)
=\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(N)$,
and finite detection on $\mathcal{I}_N$, with the promotion
$\mathcal{I}_4\to\mathcal{I}_N$ linearized by the incremental packets
of Proposition~\ref{prop:winfty-ds-stage-growth-packet}.
Proposition~\ref{prop:winfty-stage-growth-virasoro-target-contraction}
then gives the uniform target-$2$ contraction of the reduced packets
$\mathcal{J}_{M+1}^{\mathrm{red}}$ under the normalized residue
package.  The first next reduced stage is already explicit:
Corollary~\ref{cor:winfty-ds-stage5-reduced-packet} identifies
$\mathcal{J}_5^{\mathrm{red}}$ as an eleven-entry packet.

On the present theorem surface, the first live higher-spin stages are
already compressed to the stage-$3$ fifteen-coefficient packet and the
exact stage-$4$ six-entry identity packet on~$\mathcal{I}_4$, organized
as three explicit local OPE blocks.  Among those six, the only genuinely
mixed higher-spin data are
the three coefficients in the mixed $(3,4)$ block.  Within that mixed
block, the $W^{(3)}$ target channel is swap-even and the
$W^{(2)}$, $W^{(4)}$ target channels are swap-odd under reversing the
mixed OPE.  On the principal Drinfeld--Sokolov side, the mixed
$W^{(2)}$ target vanishes, while the principal
$W^{(4)}$-$W^{(4)}\to T$ coefficient is fixed to `2'.  The live
stage-$4$ comparison is therefore the exact six-entry identity packet
on~$\mathcal{I}_4$:
\[
\mathsf{C}^{\mathrm{res}}_{s,t;u;m,n}(4)
=
\mathsf{C}^{\mathrm{DS}}_{s,t;u;m,n}(4)
\]
in the channels
\[
\begin{gathered}
(3,3;4;0,2),\qquad
(4,4;4;0,4),\\
(3,4;3;0,4),\qquad
(3,4;4;0,3),\\
(4,4;2;0,6),\qquad
(3,4;2;0,5).
\end{gathered}
\]
This is exactly the first open higher-spin packet isolated abstractly
by Corollary~\ref{cor:winfty-stage4-closure-criterion}.

\subsection{\texorpdfstring{Genus-$g$ free energy}{Genus-g free energy}}\label{subsec:vir-free-energy}

\begin{theorem}[Virasoro free energy; \ClaimStatusProvedHere]\label{thm:vir-all-genera}
\textup{[Regime: curved-central
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

For the Virasoro algebra $\mathrm{Vir}_c$ at any central charge $c$, the genus-$g$ free energy is:
\begin{equation}\label{eq:vir-Fg}
F_g(\mathrm{Vir}_c) = \frac{c}{2} \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}
\end{equation}
\end{theorem}

\begin{proof}
By the genus universality theorem (Theorem~\ref{thm:genus-universality}) with $\kappa(\mathrm{Vir}_c) = c/2$ (Theorem~\ref{thm:vir-genus1-curvature}) and the Faber--Pandharipande formula (Theorem~\ref{thm:mumford-formula}).
\end{proof}

\begin{computation}[Explicit values at physical central charges]\label{comp:vir-physical-cc}
We evaluate~\eqref{eq:vir-Fg} at central charges of physical interest:

\medskip
\begin{center}
\renewcommand{\arraystretch}{1.3}
{\footnotesize
\begin{tabular}{clcccccc}
\toprule
$c$ & Model & $\kappa$ & $F_1$ & $F_2$ & $F_3$ & $F_4$ & $F_5$ \\
\midrule
$0$ & Topological & $0$ & $0$ & $0$ & $0$ & $0$ & $0$ \\[3pt]
$\frac{1}{2}$ & Ising & $\frac{1}{4}$ & $\frac{1}{96}$ & $\frac{7}{23040}$ & $\frac{31}{3870720}$ & $\frac{127}{619315200}$ & $\frac{73}{14014218240}$ \\[6pt]
$1$ & Free boson & $\frac{1}{2}$ & $\frac{1}{48}$ & $\frac{7}{11520}$ & $\frac{31}{1935360}$ & $\frac{127}{309657600}$ & $\frac{73}{7007109120}$ \\[6pt]
$25$ & Near-bosonic & $\frac{25}{2}$ & $\frac{25}{48}$ & $\frac{175}{11520}$ & $\frac{775}{1935360}$ & $\frac{127}{12386304}$ & $\frac{365}{1401421824}$ \\[6pt]
$26$ & Bosonic string & $13$ & $\frac{13}{24}$ & $\frac{91}{5760}$ & $\frac{403}{967680}$ & $\frac{1651}{154828800}$ & $\frac{949}{3503554560}$ \\[3pt]
\bottomrule
\end{tabular}
}
\end{center}

\medskip
\noindent
Three features are visible from the table.  First, $c = 0$ gives $F_g = 0$ for all~$g$: the Virasoro is uncurved, and $\mathrm{Vir}_0^! \simeq \mathrm{Vir}_0$ (Theorem~\ref{thm:virasoro-self-duality}).  Second, the $c = 26$ column gives $F_g(26) = 13 \cdot \lambda_g^{\mathrm{FP}}$, which (by complementarity) equals $F_g(0) + 13 \cdot \lambda_g^{\mathrm{FP}} = 13 \cdot \lambda_g^{\mathrm{FP}}$; in other words, $\mathrm{Vir}_{26}$ carries the \emph{entire} obstruction budget of the Koszul pair $(\mathrm{Vir}_{26}, \mathrm{Vir}_0)$.  Third, $F_g$ is linear in~$c$, so the table is determined by the single datum $\kappa = c/2$.
\end{computation}

\subsection{Non-canceling complementarity}\label{subsec:vir-complementarity}

\begin{proposition}[Virasoro complementarity; \ClaimStatusProvedHere]\label{prop:vir-complementarity}
For all $g \geq 1$:
\begin{equation}\label{eq:vir-complementarity-allgenera}
F_g(\mathrm{Vir}_c) + F_g(\mathrm{Vir}_{26-c}) = 13 \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}
\end{equation}
The right-hand side is independent of~$c$ and strictly positive for all $g \geq 1$.
\end{proposition}

\begin{proof}
The obstruction coefficients satisfy $\kappa(\mathrm{Vir}_c) + \kappa(\mathrm{Vir}_{26-c}) = c/2 + (26-c)/2 = 13$.  Since $F_g$ is linear in~$\kappa$, the sum is $13 \cdot \lambda_g^{\mathrm{FP}}$.  Positivity holds because $|B_{2g}| > 0$ and $(2^{2g-1}-1)/2^{2g-1} > 0$ for all $g \geq 1$.
\end{proof}

\begin{remark}[Structural contrast with affine Kac--Moody]\label{rem:vir-vs-km-complementarity}
\index{complementarity!non-canceling}
For KM algebras, $\kappa \propto (k + h^\vee)$ and the FF involution gives $\kappa \mapsto -\kappa$, hence $\kappa + \kappa' = 0$.  For the Virasoro, the DS parametrization $c(k)$ is nonlinear; the involution $c \mapsto 26 - c$ has fixed point $c = 13$ (at $k = -2 \pm i$), giving $\kappa + \kappa' = 13 \neq 0$.  For $\mathcal{W}_N$: $\kappa + \kappa' = 13$ ($N=2$), $250/3$ ($N=3$).
\end{remark}

\subsection{\texorpdfstring{The $c = 0$ / $c = 26$ trichotomy at all genera}{The c = 0 / c = 26 trichotomy at all genera}}\label{subsec:vir-trichotomy}

\begin{remark}[Three regimes of the Virasoro genus expansion]\label{rem:vir-trichotomy-genera}
\index{Virasoro algebra!trichotomy}
The genus-0 trichotomy extends to all genera (cf.\ Computation~\ref{comp:virasoro-curvature}):
\begin{enumerate}
\item \emph{$c = 0$.} $F_g = 0$ for all $g \geq 1$; $\bar{B}(\mathrm{Vir}_0)$ is a genuine cochain complex.
\item \emph{$c$ generic.} $F_g = (c/2) \cdot \lambda_g^{\mathrm{FP}} \neq 0$; the bar complex is curved.  The M/S-level shadow partner is $\mathrm{Vir}_{26-c}$; the H-level infinite-generator realization is the $W_\infty$ MC4 package (\S\ref{sec:principal-contributions}).  Complementarity sum: $13 \cdot \lambda_g^{\mathrm{FP}}$.
\item \emph{$c = 26$.} $F_g(\mathrm{Vir}_{26}) = 13 \cdot \lambda_g^{\mathrm{FP}}$; the partner $\mathrm{Vir}_0$ is uncurved, so $\mathrm{Vir}_{26}$ carries the entire complementarity budget.
\end{enumerate}
The generating function:
\begin{equation}\label{eq:vir-generating}
\sum_{g=1}^{\infty} F_g(\mathrm{Vir}_c)\, x^{2g} = \frac{c}{2}\left(\frac{x/2}{\sin(x/2)} - 1\right)
\end{equation}
has radius of convergence $|x| = 2\pi$.
\end{remark}

\begin{remark}[Obstruction coefficient and the bosonic string]\label{rem:vir-bosonic-string-genus}
\index{bosonic string!obstruction coefficient}
$\kappa(\mathrm{Vir}_c) = c/2$ vs.\ $\kappa(\mathcal{H}_\kappa) = \kappa$: for $c=1$, $\kappa(\mathcal{H}_1) = 1$ but $\kappa(\mathrm{Vir}_1) = 1/2$, reflecting the difference between the full algebra and its Virasoro subalgebra.  For the bosonic string:
\[
F_g^{\text{matter}} = 26 \cdot \lambda_g^{\mathrm{FP}}, \qquad
F_g^{\text{ghost}} = -13 \cdot \lambda_g^{\mathrm{FP}},
\qquad F_g^{\text{total}} = 13 \cdot \lambda_g^{\mathrm{FP}} = F_g(\mathrm{Vir}_{26}).
\]
Thus $\kappa_{\text{total}} = 13 = c_{\text{matter}}/2$ tracks the matter central charge, not $c_{\text{total}} = 0$.
\end{remark}

\section{Genus expansion for all Master Table entries}\label{sec:genus-all-master}

By the universal generating function (Theorem~\ref{thm:universal-generating-function}), every row of the Master Table (Table~\ref{tab:master-invariants}) admits an explicit genus expansion.  The Heisenberg (\S\ref{sec:frame-genus-tower}), $\widehat{\mathfrak{sl}}_2$, Virasoro, and $\mathcal{W}_3$ cases appear above.  We complete the remaining entries; each is a one-line specialization of the universal formula, with $\kappa$ as the only algebra-specific input.

\begin{computation}[\texorpdfstring{$\widehat{\mathfrak{sl}}_3$}{sl-hat_3} genus expansion]\label{comp:sl3-genus-expansion}
\index{sl3@$\mathfrak{sl}_3$!genus expansion}
For $\widehat{\mathfrak{sl}}_3$ at level~$k$ with $\kappa = 4(k+3)/3$ (Table~\ref{tab:master-invariants}):
\begin{equation}\label{eq:sl3-Fg}
F_g(\widehat{\mathfrak{sl}}_{3,k}) = \frac{4(k+3)}{3} \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}
\end{equation}
At the first nontrivial level $k = 1$: $\kappa = 16/3$.
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{ccc}
\toprule
$g$ & $F_g$ (exact) & $F_g$ (decimal) \\
\midrule
$1$ & $2/9$ & $2.22 \times 10^{-1}$ \\
$2$ & $7/1080$ & $6.48 \times 10^{-3}$ \\
$3$ & $31/181440$ & $1.71 \times 10^{-4}$ \\
$4$ & $127/29030400$ & $4.37 \times 10^{-6}$ \\
$5$ & $73/656916480$ & $1.11 \times 10^{-7}$ \\
$6$ & $1414477/502146957312000$ & $2.82 \times 10^{-9}$ \\
$7$ & $8191/114776447385600$ & $7.14 \times 10^{-11}$ \\
$8$ & $16931177/9365758106664960000$ & $1.81 \times 10^{-12}$ \\
$9$ & $5749691557/125561099481193119744000$ & $4.58 \times 10^{-14}$ \\
$10$ & $91546277357/78924119673892818124800000$ & $1.16 \times 10^{-15}$ \\
\bottomrule
\end{tabular}
\end{center}
The complementarity sum $\kappa + \kappa' = 4(k+3)/3 + 4(-k-3)/3 = 0$ vanishes, as for all affine Kac--Moody algebras.
\end{computation}

\begin{proposition}[\texorpdfstring{$\widehat{\mathfrak{sl}}_3$}{sl3-hat} complementarity; \ClaimStatusProvedHere]%
\label{prop:sl3-complementarity-all-genera}
\index{sl3@$\mathfrak{sl}_3$!complementarity}
For all $g \geq 1$:
\begin{equation}\label{eq:sl3-complementarity-allgenera}
F_g(\widehat{\mathfrak{sl}}_{3,k}) + F_g(\widehat{\mathfrak{sl}}_{3,k'}) = 0,
\qquad k' = -k-6.
\end{equation}
Moreover, $c(k) + c(k') = 16$ and
$\kappa(k) + \kappa(k') = 0$.
\end{proposition}

\begin{proof}
The central charge $c(k) = 8k/(k+3)$ satisfies
$c(k') = 8(-k-6)/(-k-3) = 8(k+6)/(k+3)$, so
$c + c' = 8k/(k+3) + 8(k+6)/(k+3) = (8k + 8k + 48)/(k+3)
= 8(2k+6)/(k+3) = 16$.
Since $\kappa = (k+h^\vee)\dim\mathfrak{g}/(2h^\vee)
= (k+3) \cdot 8/6 = 4(k+3)/3$ and
$\kappa' = 4(k'+3)/3 = 4(-k-3)/3 = -\kappa$,
the complementarity sum vanishes.
\end{proof}

\begin{computation}[Explicit \texorpdfstring{$\widehat{\mathfrak{sl}}_3$}{sl-hat_3}
values at multiple levels]\label{comp:sl3-multi-level}
\index{sl3@$\mathfrak{sl}_3$!genus expansion, multi-level}
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{cccccccc}
\toprule
$k$ & $c(k)$ & $\kappa(k)$ & $F_1$ & $F_2$ & $F_3$ & $F_4$ & $F_5$ \\
\midrule
$1$ & $2$ & $16/3$ & $2/9$ & $7/1080$ & $31/181440$ & $127/29030400$ & $73/656916480$ \\[3pt]
$2$ & $16/5$ & $20/3$ & $5/18$ & $7/864$ & $31/145152$ & $127/23224320$ & $73/525533184$ \\[3pt]
$3$ & $4$ & $8$ & $1/3$ & $7/720$ & $31/120960$ & $127/19353600$ & $73/437944320$ \\
\bottomrule
\end{tabular}
\end{center}

\noindent
At $k = 3$ (so $\kappa = 8 = \dim\mathfrak{sl}_3$), the free energy coincides
with that of a rank-$8$ lattice VOA.  The dual levels
$k' = -7, -8, -9$ give the same table with opposite signs.
At the critical level $k = -3$, the genus expansion formalism
does not apply ($\kappa = 0$, and the Sugawara construction
degenerates), but one has $F_g = 0$ for all~$g$: the critical
level is uncurved.
\end{computation}

\begin{computation}[\texorpdfstring{$\widehat{E}_8$}{E_8} genus expansion]\label{comp:e8-genus-expansion}
\index{E8@$E_8$!genus expansion}
For $\widehat{E}_8$ at level~$k$ with $\kappa = 62(k+30)/15$ (Table~\ref{tab:master-invariants}):
\begin{equation}\label{eq:e8-Fg}
F_g(\widehat{E}_{8,k}) = \frac{62(k+30)}{15} \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}
\end{equation}
At $k = 1$ (the unique integrable level for $E_8$): $\kappa = 62 \cdot 31/15 = 1922/15$.
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{ccc}
\toprule
$g$ & $F_g$ (exact) & $F_g$ (decimal) \\
\midrule
$1$ & $961/180$ & $5.34$ \\
$2$ & $6727/43200$ & $1.56 \times 10^{-1}$ \\
$3$ & $29791/7257600$ & $4.10 \times 10^{-3}$ \\
$4$ & $122047/1161216000$ & $1.05 \times 10^{-4}$ \\
$5$ & $70153/26276659200$ & $2.67 \times 10^{-6}$ \\
$6$ & $1359312397/20085878292480000$ & $6.77 \times 10^{-8}$ \\
$7$ & $7871551/4591057895424000$ & $1.71 \times 10^{-9}$ \\
$8$ & $16270861097/374630324266598400000$ & $4.34 \times 10^{-11}$ \\
$9$ & $5525453586277/5022443979247724789760000$ & $1.10 \times 10^{-12}$ \\
$10$ & $87975972540077/3156964786955712724992000000$ & $2.79 \times 10^{-14}$ \\
\bottomrule
\end{tabular}
\end{center}
The large values reflect $\dim(E_8) = 248$: the obstruction coefficient $\kappa \approx 128.1$ is among the largest in the table.
\end{computation}

\begin{computation}[General \texorpdfstring{$\mathcal{W}_N$}{W_N} genus expansion]\label{comp:wn-genus-expansion}
\index{W-algebra@$\mathcal{W}$-algebra!genus expansion, general}
For $\mathcal{W}_N^k(\mathfrak{sl}_N)$ with $\kappa = c(k) \cdot (H_N - 1)$ where $H_N = \sum_{j=1}^N 1/j$ is the $N$-th harmonic number (Theorem~\ref{thm:wn-obstruction}):
\begin{equation}\label{eq:wn-Fg}
F_g(\mathcal{W}_N^k) = c(k) \cdot (H_N - 1) \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}
\end{equation}
At genus~1, $F_1 = c(k) \cdot (H_N - 1)/24$.  The complementarity sum:
\[
\kappa(\mathcal{W}_N^k) + \kappa(\mathcal{W}_N^{k'}) = (c + c') \cdot (H_N - 1)
\]
where $c + c' = 2(N-1)(2N^2+2N+1)$ (the level-independent sum from Theorem~\ref{thm:central-charge-complementarity}).  First values:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{ccccc}
\toprule
$N$ & $H_N - 1$ & $c + c'$ & $\kappa + \kappa'$ & Decimal \\
\midrule
$2$ & $1/2$ & $26$ & $13$ & $13.00$ \\
$3$ & $5/6$ & $100$ & $250/3$ & $83.33$ \\
$4$ & $13/12$ & $246$ & $533/2$ & $266.50$ \\
$5$ & $77/60$ & $488$ & $9394/15$ & $626.27$ \\
$6$ & $29/20$ & $850$ & $2465/2$ & $1232.50$ \\
$7$ & $223/140$ & $1356$ & $75597/35$ & $2159.91$ \\
$8$ & $481/280$ & $2030$ & $13949/4$ & $3487.25$ \\
\bottomrule
\end{tabular}
\end{center}
The growth is $\kappa + \kappa' \sim N^2 \log N$ for large~$N$, reflecting $c + c' \sim 4N^3$ and $H_N - 1 \sim \log N$.
\end{computation}

\begin{computation}[Lattice VOA genus expansion at arbitrary rank]\label{comp:lattice-genus-expansion}
\index{lattice VOA!genus expansion}
For a rank-$d$ even unimodular lattice $\Lambda$ (e.g., $E_8$, $E_8 \oplus E_8$, the Leech lattice), the lattice vertex algebra $V_\Lambda \cong \mathcal{H}_1^{\otimes d}$ has obstruction coefficient $\kappa(V_\Lambda) = d$ (Corollary~\ref{cor:kappa-additivity}).  The genus-$g$ free energy:
\begin{equation}\label{eq:lattice-Fg-arbitrary-rank}
F_g(V_\Lambda) = d \cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}
\end{equation}
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{clccccc}
\toprule
$d$ & Lattice & $\kappa$ & $F_1$ & $F_2$ & $F_3$ & $F_4$ \\
\midrule
$8$ & $E_8$ & $8$ & $1/3$ & $7/720$ & $31/120960$ & $127/19353600$ \\[3pt]
$16$ & $E_8 \oplus E_8$ & $16$ & $2/3$ & $7/360$ & $31/60480$ & $127/9676800$ \\[3pt]
$24$ & Leech $\Lambda_{24}$ & $24$ & $1$ & $7/240$ & $31/40320$ & $127/6451200$ \\
\bottomrule
\end{tabular}
\end{center}
At $d = 24$ (the Leech lattice, or any Niemeier lattice), $F_1 = 1$---a remarkable integrality property.  This reflects $\kappa = 24 = c$ (the central charge of a rank-$24$ lattice VOA), so $F_1 = c/24 = 1$, the coefficient that governs the $q$-expansion of the partition function.

The complementarity is of exact cancellation type: $\kappa + \kappa' = 0$ (Proposition~\ref{prop:complementarity-classification}(i)), since $V_\Lambda^!$ is the curved commutative chiral algebra $\mathrm{Sym}^{\mathrm{ch}}(\Lambda^* \otimes \omega_X)$ with $\kappa' = -d$.
\end{computation}

%% ====================================================================
%% Free fermion genus expansion
%% ====================================================================

\section{Free fermion genus expansion}\label{sec:fermion-genera}
\index{free fermion!genus expansion}
\index{bc system@$bc$ system!genus expansion}

The $bc$ system at conformal weights $(\lambda, 1-\lambda)$
is a fermionic chiral algebra with central charge
$c_{bc} = -2(6\lambda^2 - 6\lambda + 1) = 1 - 3(2\lambda-1)^2$
(Computation~\ref{comp:beta-gamma-central-charges}).
Its Koszul dual is the bosonic $\beta\gamma$-system at the same
weights, with $c_{\beta\gamma} = 2(6\lambda^2 - 6\lambda + 1)
= -c_{bc}$, and the underlying operadic duality is
$\mathrm{Ext} \leftrightarrow \mathrm{Sym}$
(Theorem~\ref{thm:fermion-boson-koszul}).

\begin{theorem}[Free fermion free energy at all genera;
\ClaimStatusProvedHere]\label{thm:fermion-all-genera}
\index{free fermion!obstruction coefficient}
For the $bc$ system at conformal weights $(\lambda, 1-\lambda)$,
the genus-$g$ free energy is
\begin{equation}\label{eq:fermion-Fg}
F_g(bc_\lambda) = \kappa(bc_\lambda) \cdot
\frac{2^{2g-1}-1}{2^{2g-1}} \cdot
\frac{|B_{2g}|}{(2g)!}
\end{equation}
for all $g \geq 1$, where the obstruction coefficient is
\begin{equation}\label{eq:fermion-kappa}
\kappa(bc_\lambda) = \frac{c_{bc}}{2}
= -(6\lambda^2 - 6\lambda + 1).
\end{equation}
For the Koszul dual $\beta\gamma$-system,
$\kappa(\beta\gamma_\lambda) = 6\lambda^2 - 6\lambda + 1
= -\kappa(bc_\lambda)$.
\end{theorem}

\begin{proof}
By the genus universality theorem
(Theorem~\ref{thm:genus-universality}) applied to
the $bc$ system as a chiral algebra with stress-energy tensor
$T = \lambda\,(\partial b)\,c + (1-\lambda)\,b\,(\partial c)$.
The genus-$1$ curvature of the bar complex is determined by
the quartic pole $T_{(3)}T = c_{bc}/2$
(the same mechanism as Theorem~\ref{thm:vir-genus1-curvature}
applied to the Virasoro subalgebra), giving
$\kappa = c_{bc}/2 = -(6\lambda^2 - 6\lambda + 1)$.
The Faber--Pandharipande formula
(Theorem~\ref{thm:mumford-formula}) evaluates the
tautological integral.
\end{proof}

\begin{computation}[Obstruction coefficients at
special weights]\label{comp:fermion-kappa-table}
\index{bc system@$bc$ system!central charge table}
We tabulate the central charge and obstruction coefficient
for the $bc$ system at the weights of principal interest:

\medskip
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{clccc}
\toprule
$\lambda$ & System & $c_{bc}$ & $\kappa(bc)$ & $\kappa(\beta\gamma)$ \\
\midrule
$2$ & String ghosts & $-26$ & $-13$ & $13$ \\[3pt]
$1$ & Weight-$(1,0)$ & $-2$ & $-1$ & $1$ \\[3pt]
$\frac{1}{2}$ & Complex fermion & $1$ & $\frac{1}{2}$ & $-\frac{1}{2}$ \\[6pt]
$0$ & Weight-$(0,1)$ & $-2$ & $-1$ & $1$ \\[3pt]
\bottomrule
\end{tabular}
\end{center}

\medskip
\noindent
The symmetry $\kappa(bc_\lambda) = \kappa(bc_{1-\lambda})$
reflects the invariance of $6\lambda^2 - 6\lambda + 1$ under
$\lambda \mapsto 1 - \lambda$, consistent with the fact that
exchanging the roles of $b$ and~$c$ preserves the $bc$ system
up to isomorphism.
\end{computation}

\begin{proposition}[\texorpdfstring{$bc$}{bc}--\texorpdfstring{$\beta\gamma$}{beta-gamma} complementarity;
\ClaimStatusProvedHere]\label{prop:fermion-complementarity}
\index{complementarity!bc-betagamma@$bc$--$\beta\gamma$}
For all $g \geq 1$ and all conformal weights~$\lambda$:
\begin{equation}\label{eq:fermion-complementarity}
F_g(bc_\lambda) + F_g(\beta\gamma_\lambda) = 0
\end{equation}
\end{proposition}

\begin{proof}
The obstruction coefficients satisfy
$\kappa(bc_\lambda) + \kappa(\beta\gamma_\lambda)
= -(6\lambda^2 - 6\lambda + 1) + (6\lambda^2 - 6\lambda + 1) = 0$.
Since $F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$ is linear
in~$\kappa$, exact cancellation follows.
\end{proof}

\begin{remark}[Complementarity type classification]
\label{rem:fermion-complementarity-type}
The exact cancellation $\kappa + \kappa' = 0$ for $bc \leftrightarrow \beta\gamma$ matches the KM type (Proposition~\ref{prop:sl2-complementarity-all-genera}): both arise from operadic dualities ($\mathrm{Lie}/\mathrm{Com}$ and $\mathrm{Ext}/\mathrm{Sym}$) that negate~$\kappa$.  The Virasoro and $\mathcal{W}_N$ algebras ($\kappa + \kappa' \neq 0$) arise from DS reduction with nonlinear $c(k)$.
\end{remark}

\begin{computation}[Bosonic string ghost genus expansion]
\label{comp:bc-ghost-genus}
\index{bc system@$bc$ system!ghost genus expansion}
For the bosonic string ghost system ($\lambda = 2$,
$c = -26$, $\kappa = -13$), the genus-$g$ free energy
is $F_g = -13 \cdot \lambda_g^{\mathrm{FP}}$:

\medskip
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{ccccc}
\toprule
$g$ & $\lambda_g^{\mathrm{FP}}$ & $F_g(bc_2)$ & Decimal & $|F_g/F_{g-1}|$ \\
\midrule
$1$ & $\frac{1}{24}$ & $-\frac{13}{24}$ & $-0.5417$ & --- \\[6pt]
$2$ & $\frac{7}{5760}$ & $-\frac{91}{5760}$ & $-1.580 \times 10^{-2}$ & $0.02917$ \\[6pt]
$3$ & $\frac{31}{967680}$ & $-\frac{403}{967680}$ & $-4.165 \times 10^{-4}$ & $0.02636$ \\[6pt]
$4$ & $\frac{127}{154828800}$ & $-\frac{1651}{154828800}$ & $-1.066 \times 10^{-5}$ & $0.02560$ \\[6pt]
$5$ & $\frac{73}{3503554560}$ & $-\frac{949}{3503554560}$ & $-2.709 \times 10^{-7}$ & $0.02540$ \\[6pt]
$6$ & $\frac{1414477}{2678117105664000}$ & $-\frac{1414477}{206009008128000}$ & $-6.866 \times 10^{-9}$ & $0.02535$ \\[6pt]
$7$ & $\frac{8191}{612141052723200}$ & $-\frac{8191}{47087773286400}$ & $-1.740 \times 10^{-10}$ & $0.02533$ \\[6pt]
$8$ & $\frac{16931177}{49950709902213120000}$ & $-\frac{16931177}{3842362300170240000}$ & $-4.406 \times 10^{-12}$ & $0.02533$ \\[4pt]
\bottomrule
\end{tabular}
\end{center}

\medskip
\noindent
All free energies are negative ($\kappa < 0$), and the ratios
$|F_{g+1}/F_g|$ approach the universal limit
$1/(2\pi)^2 \approx 0.02533$ from above
(Proposition~\ref{prop:genus-expansion-convergence}).
The Koszul dual $\beta\gamma_2$ system ($c = 26$, $\kappa = 13$)
has $F_g(\beta\gamma_2) = -F_g(bc_2)$, with all positive
free energies.
\end{computation}

%% ====================================================================
%% Master comparison table
%% ====================================================================

\section{Master comparison table at all genera}
\label{sec:master-genus-comparison}
\index{genus expansion!master comparison}
\index{master table of invariants!genus expansion}

By the universal generating function
(Theorem~\ref{thm:universal-generating-function}), the genus-$g$
free energy of any Koszul chiral algebra takes the form
$F_g(\cA) = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}$, so the
entire scalar genus expansion is determined by the single
invariant~$\kappa$ (the separately proved spectral invariants and the
proved H-level deformation package require data beyond~$\kappa$; sharp
periodicity claims require still further input; see
Theorem~\ref{thm:spectral-characteristic} and
Definition~\ref{def:full-modular-package}).
The following table records $\kappa$, the same-family partner / dual data, and
the first three explicit free energies.

\begin{table}[ht]
\centering
\caption{Genus expansion for all computed chiral algebras}
\label{tab:genus-expansion-master}
\index{obstruction coefficient!comparison table}
\renewcommand{\arraystretch}{1.5}
{\small
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
\textbf{Algebra} & $c$ & $\kappa$ &
\textbf{Dual} & $\kappa'$ & $\kappa{+}\kappa'$ &
\textbf{Type} \\
\hline
\multicolumn{7}{|c|}{\textit{Free fields
  ($\mathrm{Ext} \leftrightarrow \mathrm{Sym}$ duality)}} \\
\hline
$bc_2$ (ghosts)
  & $-26$ & $-13$ & $\beta\gamma_2$
  & $13$ & $0$ & (i) \\
\hline
$bc_1$
  & $-2$ & $-1$ & $\beta\gamma_1$
  & $1$ & $0$ & (i) \\
\hline
$bc_{1/2}$ (fermion)
  & $1$ & $\frac{1}{2}$ & $\beta\gamma_{1/2}$
  & $-\frac{1}{2}$ & $0$ & (i) \\
\hline
\multicolumn{7}{|c|}{\textit{Heisenberg}} \\
\hline
$\mathcal{H}_\kappa$ ($d = 1$)
  & $1$ & $\kappa$ & $\mathrm{Sym}^{\mathrm{ch}}$
  & $-\kappa$ & $0$ & (i) \\
\hline
\multicolumn{7}{|c|}{\textit{Affine Kac--Moody
  ($k \mapsto -k - 2h^\vee$)}} \\
\hline
$\widehat{\mathfrak{sl}}_{2,k}$
  & $\frac{3k}{k{+}2}$ & $\frac{3(k{+}2)}{4}$
  & $\widehat{\mathfrak{sl}}_{2,-k-4}$
  & $\frac{3(-k{-}2)}{4}$ & $0$ & (i) \\
\hline
$\widehat{\mathfrak{sl}}_{3,k}$
  & $\frac{8k}{k{+}3}$ & $\frac{4(k{+}3)}{3}$
  & $\widehat{\mathfrak{sl}}_{3,-k-6}$
  & $\frac{4(-k{-}3)}{3}$ & $0$ & (i) \\
\hline
$\widehat{E}_{8,k}$
  & $\frac{248k}{k{+}30}$ & $\frac{62(k{+}30)}{15}$
  & $\widehat{E}_{8,-k-60}$
  & $\frac{62(-k{-}30)}{15}$ & $0$ & (i) \\
\hline
\multicolumn{7}{|c|}{\textit{$\mathcal{W}$-algebras (DS
  reduction, self-dual operad)}} \\
\hline
$\mathrm{Vir}_c$
  & $c$ & $\frac{c}{2}$
  & $\mathrm{Vir}_{26-c}$\textsuperscript{$\dagger$}
  & $\frac{26-c}{2}$ & $13$ & (ii) \\
\hline
$\mathcal{W}_3^k$
  & $c(k)$ & $\frac{5c}{6}$
  & $\mathcal{W}_3^{-k-6}$
  & $\frac{5c'}{6}$ & $\frac{250}{3}$ & (ii) \\
\hline
\multicolumn{7}{|c|}{\textit{Lattice VOAs}} \\
\hline
$V_{E_8}$ lattice
  & $8$ & $8$
  & (curved $\mathrm{Sym}^{\mathrm{ch}}$)
  & $-8$ & $0$ & (i) \\
\hline
\end{tabular}
}
\end{table}
\noindent\textsuperscript{$\dagger$}In Table~\ref{tab:genus-expansion-master},
the Virasoro entry records the proved same-family shadow partner used by
the current genus and semi-infinite calculations.  The stronger H-level
infinite-generator realization is delegated to the exact $W_\infty$
MC4 package of filtered H-level targets, residue identities, and finite
detection on $\mathcal{I}_N$, whose first live higher-spin stages are
already reduced on the theorem surface to the stage-$3$
fifteen-coefficient packet and the exact stage-$4$ six-entry identity
packet on~$\mathcal{I}_4$, splitting into the four higher-spin channels
$c_{334}$, $c_{444}$,
$\mathsf{C}_{3,4;3;0,4}$, $\mathsf{C}_{3,4;4;0,3}$ together with the
two Virasoro-target channels whose principal values are fixed.  From
there, Proposition~\ref{prop:winfty-ds-stage-growth-packet} and
Corollary~\ref{cor:winfty-ds-stage-growth-top-parity} linearize the
promotion to the full family $\mathcal{I}_N$; the first next reduced
stage is the eleven-entry packet
$\mathcal{J}_5^{\mathrm{red}}$ of
Corollary~\ref{cor:winfty-ds-stage5-reduced-packet}; and the additional
stage-$4$ contraction to four channels requires the missing
Ward-inheritance lemma isolated as
Conjecture~\ref{conj:winfty-stage4-ward-inheritance}.

\begin{table}[ht]
\centering
\caption{Explicit free energies $F_1, \ldots, F_5$
for representative levels}
\label{tab:genus-expansion-values}
\renewcommand{\arraystretch}{1.5}
{\footnotesize
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
\textbf{Algebra} & $\kappa$ & $F_1$ & $F_2$ & $F_3$ & $F_4$ & $F_5$ \\
\hline
$\mathcal{H}_1$
  & $1$ & $\frac{1}{24}$ & $\frac{7}{5760}$ & $\frac{31}{967680}$
  & $\frac{127}{154828800}$ & $\frac{73}{3503554560}$ \\
\hline
$bc_2$ (ghosts)
  & $-13$ & $-\frac{13}{24}$ & $-\frac{91}{5760}$ & $-\frac{403}{967680}$
  & $-\frac{1651}{154828800}$ & $-\frac{949}{3503554560}$ \\[2pt]
\hline
$bc_{1/2}$ (fermion)
  & $\frac{1}{2}$ & $\frac{1}{48}$ & $\frac{7}{11520}$ & $\frac{31}{1935360}$
  & $\frac{127}{309657600}$ & $\frac{73}{7007109120}$ \\[4pt]
\hline
$\beta\gamma_1$
  & $1$ & $\frac{1}{24}$ & $\frac{7}{5760}$ & $\frac{31}{967680}$
  & $\frac{127}{154828800}$ & $\frac{73}{3503554560}$ \\
\hline
$\widehat{\mathfrak{sl}}_{2,1}$
  & $\frac{9}{4}$ & $\frac{3}{32}$ & $\frac{7}{2560}$ & $\frac{31}{430080}$
  & $\frac{127}{68812800}$ & $\frac{73}{1557135360}$ \\[4pt]
\hline
$\widehat{\mathfrak{sl}}_{3,1}$
  & $\frac{16}{3}$ & $\frac{2}{9}$ & $\frac{7}{1080}$ & $\frac{31}{181440}$
  & $\frac{127}{29030400}$ & $\frac{73}{656916480}$ \\[4pt]
\hline
$\mathrm{Vir}_{26}$
  & $13$ & $\frac{13}{24}$ & $\frac{91}{5760}$ & $\frac{403}{967680}$
  & $\frac{1651}{154828800}$ & $\frac{949}{3503554560}$ \\
\hline
$\mathrm{Vir}_{1/2}$ (Ising)
  & $\frac{1}{4}$ & $\frac{1}{96}$ & $\frac{7}{23040}$ & $\frac{31}{3870720}$
  & $\frac{127}{619315200}$ & $\frac{73}{14014218240}$ \\[4pt]
\hline
$V_{E_8}$ lattice
  & $8$ & $\frac{1}{3}$ & $\frac{7}{720}$ & $\frac{31}{120960}$
  & $\frac{127}{19353600}$ & $\frac{73}{437944320}$ \\
\hline
$\mathcal{W}_3^1$
  & $-\frac{130}{3}$ & $-\frac{65}{36}$ & $-\frac{91}{1728}$ & $-\frac{403}{290304}$
  & $-\frac{1651}{46448640}$ & $-\frac{949}{1051066368}$ \\[4pt]
\hline
\end{tabular}
}
\end{table}

\begin{proposition}[Classification of complementarity types;
\ClaimStatusProvedHere]\label{prop:complementarity-classification}
\index{complementarity!classification of types}
For Koszul chiral algebras, the complementarity sum
$\kappa(\cA) + \kappa(\cA^!)$ falls into one of three types:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Exact cancellation}
($\kappa + \kappa' = 0$):
affine Kac--Moody algebras $\widehat{\fg}_k$,
Heisenberg $\mathcal{H}_\kappa$,
$\mathrm{Ext}/\mathrm{Sym}$ pairs
($bc \leftrightarrow \beta\gamma$),
and lattice VOAs.  In each case, the level-shift involution
acts linearly on~$\kappa$, sending
$\kappa \mapsto -\kappa$.
\item \emph{Nonzero constant}
($\kappa + \kappa' = \text{const} \neq 0$):
Virasoro ($\kappa + \kappa' = 13$),
$\mathcal{W}_3$ ($\kappa + \kappa' = 250/3$),
and general $\mathcal{W}_N$
($\kappa + \kappa' = (c+c')(H_N - 1)$).
The constant depends on the Lie algebra and the
operadic structure, but not on the level.
\item \emph{Zero by triviality}:
algebras with $c = 0$ (topological), where
$\kappa = \kappa' = 0$ and $F_g = 0$ for all~$g$.
\end{enumerate}
\end{proposition}

\begin{proof}
Type~(i):  For affine Kac--Moody, $\kappa(\widehat{\fg}_k)
= (k + h^\vee) d / (2h^\vee)$
(Table~\ref{tab:master-invariants}).  The Feigin--Frenkel
involution $k \mapsto -k - 2h^\vee$ sends
$k + h^\vee \mapsto -(k + h^\vee)$, so
$\kappa \mapsto -\kappa$ and $\kappa + \kappa' = 0$.
The same argument applies to the Heisenberg ($\kappa \mapsto
-\kappa$ under the sign change of the pairing) and to
$bc \leftrightarrow \beta\gamma$ (where
$\kappa(bc) = -\kappa(\beta\gamma)$ by
Theorem~\ref{thm:fermion-all-genera}).

Type~(ii): For $\mathcal{W}_N$,
$\kappa = c \cdot (H_N - 1)$
(Theorem~\ref{thm:wn-obstruction}).
Since $c + c'$ is level-independent
(Theorem~\ref{thm:central-charge-complementarity}),
$\kappa + \kappa' = (c + c')(H_N - 1)$ is a constant
depending only on~$\fg$.

Type~(iii): If $c(\cA) = 0$, then $\kappa = 0$ by the
relation $\kappa = c/2$ (for the Virasoro subalgebra).
\end{proof}

\begin{theorem}[Complementarity sum as root datum invariant; \ClaimStatusProvedHere]
\label{thm:complementarity-root-datum}
\index{complementarity!root datum invariant}
\index{obstruction coefficient!complementarity sum}
For any Koszul pair arising from a simple Lie algebra $\mathfrak{g}$ via the constructions of this monograph, the complementarity sum $\kappa(\mathcal{A}) + \kappa(\mathcal{A}^!)$ is a level-independent invariant of the root datum:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Affine Kac--Moody:} $\kappa(\widehat{\mathfrak{g}}_k) + \kappa(\widehat{\mathfrak{g}}_{k'}) = 0$ \textup{(}exact cancellation\textup{)}.
\item \emph{Principal $\mathcal{W}$-algebra for $\mathfrak{sl}_N$:}
\begin{equation}\label{eq:wn-kappa-sum-general}
\kappa(\mathcal{W}_N^k) + \kappa(\mathcal{W}_N^{k'}) = 2(N{-}1)(2N^2{+}2N{+}1) \cdot (H_N - 1)
\end{equation}
where $H_N - 1 = \sum_{j=2}^N 1/j$.
\item \emph{General $\mathcal{W}(\mathfrak{g}, f_{\mathrm{prin}})$:}
\begin{equation}\label{eq:general-w-kappa-sum}
\kappa(\mathcal{W}^k(\mathfrak{g})) + \kappa(\mathcal{W}^{k'}(\mathfrak{g})) = (c + c') \cdot \varrho(\mathfrak{g})
\end{equation}
where $\varrho(\mathfrak{g}) = \sum_{i=1}^r 1/(m_i + 1)$ depends only on the exponents $m_1, \ldots, m_r$ of $\mathfrak{g}$, and $c + c'$ is level-independent \textup{(}Theorem~\textup{\ref{thm:central-charge-complementarity})}.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(i) is proved in Proposition~\ref{prop:sl2-complementarity-all-genera}: $\kappa(\widehat{\mathfrak{g}}_k) = (k+h^\vee) d / (2h^\vee)$ is linear in $k+h^\vee$, so the Feigin--Frenkel involution $k \mapsto k' = -k-2h^\vee$ sends $\kappa \mapsto -\kappa$.

Parts~(ii)--(iii): by Theorem~\ref{thm:wn-obstruction} and Corollary~\ref{cor:general-w-obstruction}, $\kappa = c \cdot \varrho(\mathfrak{g})$ where $\varrho(\mathfrak{g}) = \sum 1/(m_i+1)$ depends only on $\mathfrak{g}$.  Therefore $\kappa + \kappa' = (c+c') \cdot \varrho(\mathfrak{g})$.  The sum $c + c'$ is level-independent by Theorem~\ref{thm:central-charge-complementarity}: under $k \mapsto k' = -k-2h^\vee$, the $k$-dependent terms in the central charge formula cancel.  For $\mathfrak{sl}_N$: $\varrho = H_N - 1$ and $c+c' = 2(N-1)(2N^2+2N+1)$ (Table~\ref{tab:master-invariants}).
\end{proof}

\begin{computation}[Complementarity sums for classical and exceptional types]
\label{comp:complementarity-classical}
\index{complementarity!classical types}
We list $\varrho(\mathfrak{g})$ for all simple types:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lccl}
\toprule
$\mathfrak{g}$ & $\dim(\mathfrak{g})$ & $\varrho(\mathfrak{g})$ & $c_{\mathrm{KM}} + c_{\mathrm{KM}}'$ \\
\midrule
$A_1 = \mathfrak{sl}_2$ & $3$ & $1/2$ & $6$ \\
$A_2 = \mathfrak{sl}_3$ & $8$ & $5/6$ & $16$ \\
$A_3 = \mathfrak{sl}_4$ & $15$ & $13/12$ & $30$ \\
$B_2 = \mathfrak{so}_5$ & $10$ & $3/4$ & $20$ \\
$G_2$ & $14$ & $2/3$ & $28$ \\
$F_4$ & $52$ & $7/8$ & $104$ \\
$E_6$ & $78$ & $427/360$ & $156$ \\
$E_7$ & $133$ & $2777/2520$ & $266$ \\
$E_8$ & $248$ & $121/126$ & $496$ \\
\bottomrule
\end{tabular}
\end{center}
The affine KM complementarity sum $c_{\mathrm{KM}} + c_{\mathrm{KM}}' = 2\dim(\mathfrak{g})$ is listed for reference.  The $\mathcal{W}$-algebra complementarity sum $\kappa + \kappa' = (c_W + c_W') \cdot \varrho$ requires the DS central charge sum $c_W + c_W'$, which is $2\dim(\mathfrak{g}) - 2c_{\mathrm{ghost}}$ with $c_{\mathrm{ghost}}$ depending on the principal sl$_2$ embedding.  For $\mathfrak{sl}_N$, $c_W + c_W' = 2(N-1)(2N^2+2N+1)$.
\end{computation}

\begin{remark}[Operadic origin of the trichotomy]
\label{rem:complementarity-operadic}
\index{operadic structure!complementarity type}
Type~(i) ($\kappa + \kappa' = 0$) arises from $\mathrm{Lie}/\mathrm{Com}$ or $\mathrm{Ext}/\mathrm{Sym}$ duality, where the operadic Koszul involution acts linearly on $\kappa$.  Type~(ii) ($\kappa + \kappa' \neq 0$) arises from DS reduction, whose nonlinear parametrization $c(k)$ prevents negation.  Type~(iii) is degenerate ($\kappa = \kappa' = 0$).
\end{remark}

%% ====================================================================
%% Genus expansion at special levels
%% ====================================================================

\section{Genus expansion at special levels}
\label{sec:special-level-genera}
\index{genus expansion!special levels}

At distinguished values of the level or central charge, the
genus expansion exhibits qualitatively different behavior:
collapse to zero (critical level), rational values of
physical interest (integrable levels), or duality pairings
between minimal models and their Virasoro complements.

\begin{computation}[\texorpdfstring{$\widehat{\mathfrak{sl}}_2$}{sl-hat_2} at level \texorpdfstring{$k = 1$}{k = 1}]
\label{comp:sl2-k1-genera}
\index{sl2@$\mathfrak{sl}_2$!integrable level $k{=}1$}
At the first integrable level $k = 1$, the central charge is
$c = 3 \cdot 1/(1+2) = 1$ and the obstruction coefficient
is $\kappa = 3(1+2)/4 = 9/4$.  The genus-$g$ free energy:
\[
F_g(\widehat{\mathfrak{sl}}_{2,1}) = \frac{9}{4}
\cdot \frac{2^{2g-1}-1}{2^{2g-1}} \cdot
\frac{|B_{2g}|}{(2g)!}
\]
Numerical values:
$F_1 = 3/32 \approx 0.0938$,
$F_2 = 7/2560 \approx 0.00273$,
$F_3 = 31/430080 \approx 7.21 \times 10^{-5}$.
\end{computation}

\begin{computation}[\texorpdfstring{$\widehat{\mathfrak{sl}}_2$}{sl-hat_2} at critical
level \texorpdfstring{$k = -2$}{k = -2}]
\label{comp:sl2-critical-genera}
\index{sl2@$\mathfrak{sl}_2$!critical level}
\index{critical level!vanishing genus expansion}
At the critical level $k = -h^\vee = -2$, the obstruction
coefficient vanishes: $\kappa = 3(-2+2)/4 = 0$.  Therefore
\begin{equation}\label{eq:sl2-critical-vanishing}
F_g(\widehat{\mathfrak{sl}}_{2,-2}) = 0
\quad \text{for all } g \geq 1.
\end{equation}
The bar complex $\bar{B}(\widehat{\mathfrak{sl}}_{2,-2})$
is a strict (uncurved) cochain complex at every genus.
This is the algebraic manifestation of the Feigin--Frenkel
center: at critical level, the bar differential satisfies
$\dfib^{\,2} = 0$ without corrections (since $\kappa = 0$ at critical level), and the cohomology recovers
$\mathfrak{z}(\widehat{\mathfrak{sl}}_{2,-2})$
(Proposition~\ref{prop:km-bar-curvature}).
\end{computation}

\begin{computation}[Virasoro at \texorpdfstring{$c = 1/2$}{c = 1/2} (Ising model)]
\label{comp:vir-ising-genera}
\index{Ising model!genus expansion}
\index{Virasoro algebra!Ising model}
At the Ising model central charge $c = 1/2$
(minimal model $(3,4)$), the obstruction coefficient is
$\kappa = 1/4$.  The genus-$g$ free energy:
\begin{equation}\label{eq:ising-Fg}
F_g(\mathrm{Vir}_{1/2}) = \frac{1}{4}
\cdot \lambda_g^{\mathrm{FP}}
\end{equation}
Numerical values:
$F_1 = 1/96 \approx 0.0104$,
$F_2 = 7/23040 \approx 3.04 \times 10^{-4}$,
$F_3 = 31/3870720 \approx 8.01 \times 10^{-6}$.
The same-family shadow partner is $\mathrm{Vir}_{51/2}$, with
$\kappa' = 51/4$ and
$F_g(\mathrm{Vir}_{51/2}) = (51/4) \cdot
\lambda_g^{\mathrm{FP}}$.  The complementarity sum
$\kappa + \kappa' = 1/4 + 51/4 = 13$ is the universal
Virasoro constant.
\end{computation}

\begin{computation}[The Ising model shadow tower: from OPE to
modular geometry]
\label{comp:ising-shadow-tower}
\index{Ising model!shadow tower}
\index{shadow tower!Ising model}
\index{Chriss--Ginzburg!Ising model as paradigm}
We build the finite-order shadow tower for the
Ising model $\mathrm{Vir}_{1/2}$ from its OPE, constructing
the ambient complementarity data through arity~$4$ under the
standing perfectness hypotheses.  This single
example realises the proved finite-order structures of the theory.

\medskip\noindent\textbf{Step 1: OPE data.}
$T(z)T(w) \sim \frac{c/2}{(z-w)^4} + \frac{2T(w)}{(z-w)^2}
+ \frac{\partial T(w)}{z-w}$
with $c = 1/2$.

\medskip\noindent\textbf{Step 2: Hessian from the quartic pole.}
$H_{\mathrm{Ising}} = (c/2)x^2 = \frac{1}{4}x^2$,
propagator $P = 2/c = 4$.

\medskip\noindent\textbf{Step 3: Cubic shadow from the quadratic
pole.}  $T_{(1)}T = 2T$, so
$\mathfrak{C}_{\mathrm{Ising}} = 2x^3$.  The cubic action is
$\frac{1}{6}\mathfrak{C}(a,a,a) = \frac{1}{3}a^3$.

\medskip\noindent\textbf{Step 4: Quartic contact from the regular
part.}
The quasi-primary composite
$\Lambda = {:}TT{:} - \frac{3}{10}\partial^2 T$ at $c = 1/2$
has BPZ norm
$\langle\Lambda|\Lambda\rangle = c(5c+22)/10
= \frac{1}{2}\cdot\frac{49/2}{10} = \frac{49}{40}$.
The quartic contact coefficient is
\begin{equation}\label{eq:ising-quartic-contact}
\mathfrak{Q}^{\mathrm{contact}}_{\mathrm{Ising}}
= \frac{10}{c(5c+22)}
= \frac{10}{\frac{1}{2}\cdot\frac{49}{2}}
= \frac{10}{49/4}
= \frac{40}{49}.
\end{equation}

\medskip\noindent\textbf{Step 5: Complementarity potential.}
\begin{equation}\label{eq:ising-complementarity-potential}
S_{\mathrm{Ising}}(x)
= \frac{1}{8}x^2
+ \frac{1}{3}x^3
+ \frac{40}{49 \cdot 24}\,x^4
+ \operatorname{Sh}_5\,x^5 + \cdots
= \frac{1}{8}x^2
+ \frac{1}{3}x^3
+ \frac{5}{147}\,x^4
+ \cdots
\end{equation}
This is \textbf{non-polynomial}: the quintic is forced nonzero by
$\mathfrak{o}^{(5)} = \{\mathfrak{C},\mathfrak{Q}\}_H \neq 0$
(Theorem~\ref{thm:w-virasoro-quintic-forced}).

\medskip\noindent\textbf{Step 6: Quartic obstruction.}
$\mathfrak{o}^{(4)}_{\mathrm{Ising}}
= \frac{1}{2}\{\mathfrak{C},\mathfrak{C}\}_H$:
\[
\{\mathfrak{C},\mathfrak{C}\}_H
= \text{(one channel on rank-1 space)}
= P \cdot (2)^2 \cdot \text{(combinatorial)}
= 4 \cdot 4 \cdot (\text{parity coeff}).
\]
By the quartic master equation
$\nabla_H\mathfrak{Q} + \mathfrak{o}^{(4)} = 0$
(Theorem~\ref{thm:nms-shadow-master-equations}), the quartic is
determined by the cubic.  The contact coefficient
$\mathfrak{Q}^{\mathrm{contact}} = 40/49$ absorbs this
obstruction.

\medskip\noindent\textbf{Step 7: Genus-$1$ Hessian correction.}
Apply the genus loop operator
$\Lambda_P(\mathfrak{Q}\,x^4) = \binom{4}{2}\cdot P \cdot
\mathfrak{Q}\,x^2$:
\begin{equation}\label{eq:ising-genus1-hessian}
\delta H^{(1)}_{\mathrm{Ising}}
= 6 \cdot 4 \cdot \frac{40}{49}\,x^2
= \frac{960}{49}\,x^2.
\end{equation}
The loop ratio is
$\rho^{(1)}_{\mathrm{Ising}}
= \delta H^{(1)}/H^{(0)}
= \frac{960/49}{1/4}
= \frac{3840}{49}
\approx 78.4$.
This is the first tensorial modular invariant beyond $\kappa$
for the Ising model: \emph{no scalar genus expansion can see it}.

\medskip\noindent\textbf{Step 8: The Koszul dual.}
The Koszul dual is $\mathrm{Vir}_{1/2}^! = \mathrm{Vir}_{51/2}$
with $\kappa' = 51/4$.  The Legendre dual potential is
$S^{\vee}(p) = \frac{1}{2}H^{-1}(p,p)
- \frac{1}{6}\mathfrak{C}(H^{-1}p, H^{-1}p, H^{-1}p) + \cdots
= 2p^2 - \tfrac{1}{6}\cdot 2 \cdot(4p)^3 + \cdots$
with $H^{-1} = P = 4$.  Concretely:
$S^{\vee}(p) = 2p^2 - \frac{64}{3}p^3 + O(p^4)$.
The cubic shadow of the dual is
$\mathfrak{C}^! = -\mathfrak{C} \cdot P^3
= -2 \cdot 64 = -128$,
confirming Proposition~\ref{prop:legendre-duality-cubic} (the Hessian-transported negative).

\medskip\noindent\textbf{Step 9: Resonance.}
The quartic resonance divisor for $\mathrm{Vir}_c$ is the pole
locus $c(5c+22) = 0$.  At $c = 1/2$, $c(5c+22) = (1/2)(49/2)
= 49/4 \neq 0$: the Ising model is \emph{quartic-regular}.
The shadow geometry is non-degenerate.

\medskip\noindent\textbf{Step 10: The phase index.}
$\nu_{\mathrm{nl}}(\mathrm{Ising}) = 3$: the cubic is the
leading nonlinear jet.  The Ising model is in the
\emph{mixed cubic--quartic phase} --- both $\mathfrak{C}$ and
$\mathfrak{Q}$ are nonzero, and the shadow tower is infinite.

\medskip
Every structure in the ambient modular complementarity package
--- the complementarity potential, the Lagrangian geometry, the
shadow jets, the quartic obstruction, the genus-$1$ correction,
the Legendre dual, the resonance class, the phase index --- is
visible in this single algebra from its OPE at $c = 1/2$.
\end{computation}

\begin{computation}[Virasoro at \texorpdfstring{$c = 25$}{c = 25}]
\label{comp:vir-c25-genera}
\index{Virasoro algebra!$c{=}25$}
At $c = 25$, the obstruction coefficient is
$\kappa = 25/2$.  This is the same-family partner of
$\mathrm{Vir}_1$ (the free boson Sugawara Virasoro,
$\kappa' = 1/2$), with complementarity sum
$25/2 + 1/2 = 13$.  The genus-$g$ free energy:
\[
F_g(\mathrm{Vir}_{25}) = \frac{25}{2}
\cdot \lambda_g^{\mathrm{FP}}
\]
Numerical values:
$F_1 = 25/48 \approx 0.521$,
$F_2 = 35/2304 \approx 0.0152$,
$F_3 = 155/387072 \approx 4.00 \times 10^{-4}$.
\end{computation}

\begin{remark}[Minimal model genus expansions]
\label{rem:minimal-model-genera}
\index{minimal model!genus expansion}
At $c_{p,q} = 1 - 6(p-q)^2/(pq)$, $F_g = (c_{p,q}/2) \cdot \lambda_g^{\mathrm{FP}}$.  The same-family partner $c' = 26 - c_{p,q}$ is never a minimal model: Ising $c=1/2 \leftrightarrow c'=51/2$; Tricritical Ising $c=7/10 \leftrightarrow c'=253/10$; Potts $c=4/5 \leftrightarrow c'=126/5$.  In all cases $\kappa + \kappa' = 13$ (Proposition~\ref{prop:vir-complementarity}), with the minimal model carrying a small fraction ($c_{p,q}/26 \ll 1$).
\end{remark}

%% ====================================================================
%% Growth rate analysis
%% ====================================================================

\section{Growth rate analysis}\label{sec:growth-rate-genera}
\index{genus expansion!growth rate}
\index{convergence!genus expansion}

Since every genus expansion takes the factored form
$F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$
(Theorem~\ref{thm:universal-generating-function}), the
growth rate $|F_{g+1}/F_g|$ is independent of the algebra
and equals the ratio
$\lambda_{g+1}^{\mathrm{FP}}/\lambda_g^{\mathrm{FP}}$.

\begin{proposition}[Universal growth rate;
\ClaimStatusProvedHere]\label{prop:universal-growth-rate}
\index{growth rate!universal limit}
For any Koszul chiral algebra $\cA$ with $\kappa(\cA) \neq 0$:
\begin{equation}\label{eq:universal-growth-rate}
\frac{|F_{g+1}(\cA)|}{|F_g(\cA)|}
= \frac{\lambda_{g+1}^{\mathrm{FP}}}
{\lambda_g^{\mathrm{FP}}}
\;\longrightarrow\; \frac{1}{(2\pi)^2}
\quad \text{as } g \to \infty.
\end{equation}
The genus expansion $\sum_{g=1}^\infty F_g(\cA)$
converges absolutely with radius of convergence $2\pi$
in the variable~$x$ of the generating function~\eqref{eq:universal-generating-function}, independent
of~$\cA$.
\end{proposition}

\begin{proof}
The Faber--Pandharipande coefficient is
$\lambda_g^{\mathrm{FP}} = \frac{2^{2g-1}-1}{2^{2g-1}}
\cdot \frac{|B_{2g}|}{(2g)!}$.  The ratio:
\[
\frac{\lambda_{g+1}^{\mathrm{FP}}}
{\lambda_g^{\mathrm{FP}}}
= \frac{2^{2g+1}-1}{2^{2g+1}} \cdot
\frac{2^{2g-1}}{2^{2g-1}-1} \cdot
\frac{|B_{2g+2}|}{|B_{2g}|} \cdot
\frac{(2g)!}{(2g+2)!}
\]
The first two factors tend to~$1$.  By the asymptotic
formula $|B_{2g}| \sim 2(2g)!/(2\pi)^{2g}$
(from $\zeta(2g) \to 1$):
\begin{align*}
\frac{|B_{2g+2}|}{|B_{2g}|} \cdot
\frac{(2g)!}{(2g+2)!}
&\;\sim\;
\frac{2(2g{+}2)!\,/\,(2\pi)^{2g+2}}{2(2g)!\,/\,(2\pi)^{2g}}
\cdot \frac{(2g)!}{(2g{+}2)!}\\[3pt]
&= \frac{1}{(2\pi)^2}
\end{align*}
giving the limit~\eqref{eq:universal-growth-rate}.
The radius of convergence of the generating function
$\sum \lambda_g^{\mathrm{FP}} x^{2g} = (x/2)/\sin(x/2) - 1$
is determined by the first singularity
of~$(x/2)/\sin(x/2)$, namely the zero of
$\sin(x/2)$ at~$x = 2\pi$.
\end{proof}

\begin{computation}[Explicit growth ratios]\label{comp:growth-ratios}
\index{growth rate!numerical values}
The ratio $\lambda_{g+1}^{\mathrm{FP}} /
\lambda_g^{\mathrm{FP}}$, which equals
$|F_{g+1}/F_g|$ for any algebra, converges rapidly to
$1/(2\pi)^2 \approx 0.02533$:

\medskip
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{ccc}
\toprule
$g$ & $\lambda_{g+1}^{\mathrm{FP}} /
\lambda_g^{\mathrm{FP}}$ & $\text{ratio} - 1/(2\pi)^2$ \\
\midrule
$1$ & $0.02917$ & $3.84 \times 10^{-3}$ \\
$2$ & $0.02636$ & $1.03 \times 10^{-3}$ \\
$3$ & $0.02560$ & $2.75 \times 10^{-4}$ \\
$4$ & $0.02540$ & $7.14 \times 10^{-5}$ \\
$5$ & $0.02535$ & $1.82 \times 10^{-5}$ \\
$6$ & $0.02534$ & $4.60 \times 10^{-6}$ \\
$7$ & $0.02533$ & $1.15 \times 10^{-6}$ \\
$8$ & $0.02533$ & $2.89 \times 10^{-7}$ \\
$9$ & $0.02533$ & $7.24 \times 10^{-8}$ \\
\bottomrule
\end{tabular}
\end{center}

\medskip
\noindent
The convergence to the limit is geometric: the error
at step~$g$ is $O(1/4^g)$, reflecting the next-to-leading
correction $\zeta(2g) = 1 + 1/4^g + O(1/9^g)$ in the
asymptotic expansion of $|B_{2g}|$.
\end{computation}

\begin{remark}[Contrast with string theory amplitudes]
\label{rem:growth-vs-string}
\index{string amplitudes!growth rate contrast}
Our genus expansion converges geometrically ($|F_g| \sim 2|\kappa|/(2\pi)^{2g}$), in sharp contrast with string amplitudes which grow as $(2g)!$ and diverge (Remark~\ref{rem:convergence-vs-string}).  The distinction: $F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$ extracts a \emph{single} tautological intersection number, while string amplitudes integrate over all of $\overline{\mathcal{M}}_g$ with all $\lambda$-classes.  The factored form shows the algebra contributes only through~$\kappa$, with the decay rate universal (Theorem~\ref{thm:genus-universality}).
\end{remark}

%% ====================================================================
%% Multiplicative genus
%% ====================================================================

\section{Multiplicative genus from Koszul duality}\label{sec:multiplicative-genus}
\index{multiplicative genus|textbf}
\index{genus expansion!multiplicative genus}

The Heisenberg generating function $\sum_g F_g x^{2g} = k \cdot ((x/2)/\sin(x/2) - 1)$ from \S\ref{sec:frame-genus-tower} was a product of two factors: the curvature $\kappa = k$ and a universal series in~$x$.  This factorization persists for every algebra in the Master Table; the universal factor is the modified Todd class.

\begin{proposition}[Koszul duality determines a multiplicative genus; \ClaimStatusProvedHere]
\label{prop:multiplicative-genus}
Every Koszul chiral algebra $\mathcal{A}$ determines a multiplicative sequence via the generating function of Theorem~\textup{\ref{thm:universal-generating-function}}:
\begin{equation}\label{eq:multiplicative-genus}
\phi_{\mathcal{A}}(x) = \kappa(\mathcal{A}) \cdot \frac{x/2}{\sin(x/2)}
\end{equation}
This is the modified Todd class \textup{(}up to the additive constant $-\kappa$\textup{)}, related to the $\hat{A}$-genus by $x \mapsto ix$:
\begin{equation}
\hat{A}(x) = \frac{x/2}{\sinh(x/2)} \;=\; \phi_{\mathcal{A}}(ix)/\kappa.
\end{equation}
\end{proposition}

\begin{proof}
The generating function $\sum_{g \geq 1} F_g x^{2g} = \kappa \cdot ((x/2)/\sin(x/2) - 1)$ (Theorem~\ref{thm:universal-generating-function}) identifies $\phi_{\mathcal{A}}(x) = \kappa + \sum_{g \geq 1} F_g x^{2g} = \kappa \cdot (x/2)/\sin(x/2)$.  The function $(x/2)/\sin(x/2)$ is the generating function of the modified Todd class: its Taylor coefficients $\frac{2^{2g-1}-1}{2^{2g-1}} \cdot \frac{|B_{2g}|}{(2g)!}$ are the Faber--Pandharipande integrals $\lambda_g^{\mathrm{FP}}$.  The relation $\sin(ix) = i\sinh(x)$ gives $(x/2)/\sin(x/2)|_{x \mapsto ix} = (ix/2)/(i\sinh(x/2)) = (x/2)/\sinh(x/2) = \hat{A}(x)$.
\end{proof}

\begin{corollary}[Koszul complementarity of genera; \ClaimStatusProvedHere]
\label{cor:complementary-genera}
\index{multiplicative genus!complementarity}
For a Koszul pair $(\mathcal{A}, \mathcal{A}^!)$:
\begin{equation}\label{eq:genus-complementarity}
\phi_{\mathcal{A}}(x) + \phi_{\mathcal{A}^!}(x) = (\kappa + \kappa') \cdot \frac{x/2}{\sin(x/2)}
\end{equation}
The right-hand side depends only on the root datum \textup{(}Theorem~\textup{\ref{thm:complementarity-root-datum})}.  For affine Kac--Moody algebras \textup{(}$\kappa + \kappa' = 0$\textup{)}, the complementary genera cancel: $\phi_{\mathcal{A}} = -\phi_{\mathcal{A}^!}$.  For Virasoro \textup{(}$\kappa + \kappa' = 13$\textup{)}, the sum is $13 \cdot (x/2)/\sin(x/2)$.
\end{corollary}

\begin{proof}
Immediate from $\phi_{\mathcal{A}} = \kappa \cdot (x/2)/\sin(x/2)$ and linearity in~$\kappa$.
\end{proof}

\begin{remark}[Relation to index theory]\label{rem:genus-index-theory}
\index{index theory!genus expansion}
The appearance of the modified Todd class $(x/2)/\sin(x/2)$ (rather than the $\hat{A}$-genus $(x/2)/\sinh(x/2)$) reflects the \emph{positive} Faber--Pandharipande coefficients: all $\lambda_g^{\mathrm{FP}} > 0$ (Remark~\ref{rem:A-hat-genus}).  In the Atiyah--Singer framework, the $\hat{A}$-genus governs the Dirac operator and has alternating signs.  The Wick rotation $x \mapsto ix$ relates the two generating functions, but the underlying geometry is distinct: the genus expansion operates on the algebraic moduli space $\overline{\mathcal{M}}_g$ (with tautological intersection theory), while the $\hat{A}$-genus operates on smooth manifolds (with characteristic classes of the tangent bundle).
\end{remark}

\subsection{Koszul duality as duality of genera}\label{subsec:koszul-genera-duality}
\index{multiplicative genus!Koszul duality}

The multiplicative genus $\phi_{\cA}$ packages the genus expansion into a single
algebro-geometric invariant.  The duality pairing on genera induced by Koszul duality is not visible in the Frenkel--Gaitsgory or Costello--Gwilliam frameworks; it is specific to the bar-cobar approach.

\begin{proposition}[Koszul duality as genus involution; \ClaimStatusProvedHere]
\label{prop:koszul-genus-involution}
\index{multiplicative genus!involution}
The assignment $\mathcal{A} \mapsto \phi_{\mathcal{A}}$ defines a homomorphism
from the Grothendieck group $K_0(\mathrm{KCA})$ of Koszul chiral algebras
\textup{(}under tensor product\textup{)} to the additive group of multiplicative
sequences:
\begin{equation}\label{eq:koszul-genus-hom}
\phi_{\mathcal{A} \otimes \mathcal{B}} = \phi_{\mathcal{A}} + \phi_{\mathcal{B}}.
\end{equation}
The Koszul duality functor $\mathcal{A} \mapsto \mathcal{A}^!$ induces an
involution on genera:
\begin{equation}\label{eq:genus-involution}
\phi_{\mathcal{A}^!}(x) = -\phi_{\mathcal{A}}(x)
\qquad\text{for Kac--Moody algebras \textup{(}$\kappa + \kappa' = 0$\textup{)}},
\end{equation}
and more generally
\begin{equation}\label{eq:genus-involution-general}
\phi_{\mathcal{A}^!}(x) = (\kappa + \kappa') \cdot \frac{x/2}{\sin(x/2)} - \phi_{\mathcal{A}}(x)
\end{equation}
for arbitrary Koszul pairs.
\end{proposition}

\begin{proof}
Equation~\eqref{eq:koszul-genus-hom} follows from the additivity
$\kappa(\mathcal{A} \otimes \mathcal{B}) = \kappa(\mathcal{A}) + \kappa(\mathcal{B})$
(Corollary~\ref{cor:kappa-additivity}) and the linearity of the generating
function in~$\kappa$ (Proposition~\ref{prop:multiplicative-genus}).
Equations~\eqref{eq:genus-involution}--\eqref{eq:genus-involution-general}
restate Corollary~\ref{cor:complementary-genera}.
\end{proof}

\begin{theorem}[Genus duality determines the Koszul pair; \ClaimStatusProvedHere]
\label{thm:genus-determines-pair}
\index{multiplicative genus!determination}
\textup{[Regime: curved-central on the Koszul locus
\textup{(}Convention~\textup{\ref{conv:regime-tags})}.]}

For a Koszul chiral algebra $\mathcal{A}$ with obstruction coefficient
$\kappa \neq 0$, the genus expansion determines:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The obstruction coefficient $\kappa(\mathcal{A})$
\textup{(}from $F_1 = \kappa/24$\textup{)};
\item The central charge $c(\mathcal{A})$ whenever $\varrho(\mathfrak{g})$ is
known \textup{(}from $\kappa = c \cdot \varrho$,
Corollary~\textup{\ref{cor:general-w-obstruction})};
\item The Feigin--Frenkel dual level $k'$ for affine algebras
\textup{(}from $\kappa + \kappa' = 0$\textup{)};
\item The radius of convergence $|x| = 2\pi$
\textup{(}independent of $\mathcal{A}$,
Theorem~\textup{\ref{thm:bernoulli-universality})}.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(i): $F_1(\mathcal{A}) = \kappa \cdot \lambda_1^{\mathrm{FP}} = \kappa/24$
(Theorem~\ref{thm:genus-universality}), so $\kappa = 24 F_1$.
Part~(ii): $\kappa = c \cdot \varrho(\mathfrak{g})$ with $\varrho$ tabulated
(Remark~\ref{rem:general-w-kappa-values}), so $c = \kappa/\varrho$.
Part~(iii): The Feigin--Frenkel involution gives $k' = -k - 2h^\vee$ with
$\kappa(k') = -\kappa(k)$ (antisymmetry of the complementarity sum for
Kac--Moody algebras), determining $k'$ from $\kappa$.
Part~(iv): Theorem~\ref{thm:bernoulli-universality} (the convergence
ratio $F_{g+1}/F_g \to 1/(2\pi)^2$ is $\kappa$-independent).
\end{proof}

\begin{remark}[The genus expansion as a complete invariant]
\label{rem:genus-complete-invariant}
\index{multiplicative genus!completeness}
The genus expansion $\{F_g(\mathcal{A})\}$ determines $\kappa$, $c$, and $k'$ (hence $\mathcal{A}^!$ abstractly) but not $\mathcal{A}$ itself: e.g., $\mathcal{H}_1$ and $\mathrm{Vir}_2$ share $\kappa = 1$.  The bar cohomology generating function $P_{\mathcal{A}}(x)$ provides the additional data.
\end{remark}

\begin{computation}[Genus duality table]\label{comp:genus-duality-table}
\index{multiplicative genus!duality table}
Genus duality data for all Master Table entries.
The columns show $\kappa$, $\kappa'$, the sum $\kappa + \kappa'$
(the \emph{genus-duality invariant}), and the complementary genus
$\phi_{\cA} + \phi_{\cA^!}$.
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lcccl}
\toprule
Algebra $\mathcal{A}$ & $\kappa$ & $\kappa'$ & $\kappa + \kappa'$ & Complementary genus \\
\midrule
Heisenberg $\mathcal{H}_1$ & $1$ & $-1$ & $0$ & $0$ (antisymmetric) \\
$\widehat{\mathfrak{sl}}_{2,k}$ & $\frac{3(k+2)}{4}$ & $\frac{-3(k+2)}{4}$ & $0$ & $0$ \\
$\widehat{\mathfrak{sl}}_{3,k}$ & $\frac{4(k+3)}{3}$ & $\frac{-4(k+3)}{3}$ & $0$ & $0$ \\
$\mathrm{Vir}_c$ & $\frac{c}{2}$ & $\frac{26-c}{2}$ & $13$ & $13\phi_0$ \\
$\mathcal{W}_{3,c}$ & $\frac{5c}{6}$ & $\frac{5(100-c)}{6}$ & $\frac{250}{3}$ & $\frac{250}{3}\phi_0$ \\
$\widehat{E}_{8,k}$ & $\frac{62(k+30)}{15}$ & $\frac{-62(k+30)}{15}$ & $0$ & $0$ \\
\bottomrule
\end{tabular}
\end{center}
where $\phi_0(x) = (x/2)/\sin(x/2)$ is the universal generating function.
For all Kac--Moody algebras, the complementary genus vanishes
\textup{(}$\kappa + \kappa' = 0$\textup{)}: the genus expansion is an
\emph{antisymmetric} function of the Koszul pair.  For Virasoro and
$\mathcal{W}$-algebras, the nonvanishing sum $\kappa + \kappa'$ is
a root-datum invariant
\textup{(}Theorem~\textup{\ref{thm:complementarity-root-datum})}.
\end{computation}

% Section summary removed (content in concordance).

\section{From genus expansions to knot invariants}
\label{sec:genus-knot-invariants}
\index{knot invariants!from genus expansions}
\index{weight systems}

The genus tower $\{F_g(\cA)\}_{g \geq 0}$ connects to finite-type
knot invariants through the Fulton--MacPherson propagator integrals
that underlie both constructions.

\begin{remark}[Genus-\texorpdfstring{$0$}{0} bar complex and weight systems]
\label{rem:genus-0-weight-systems}
The genus-$0$ bar complex of a Koszul chiral algebra $\cA$
produces weight systems via the same configuration space integrals
on $\overline{C}_n(\mathbb{P}^1)$ that compute the genus-$0$
expansion $F_0$.  Concretely, the FM propagator
$\omega = d\log(z_1 - z_2)$ on the boundary strata of
$\overline{C}_n(\mathbb{P}^1)$ assigns to each chord diagram
an element of $H^*(\bar{B}^{\mathrm{ch}}(\cA))$, yielding
finite-type knot invariants
(Theorem~\ref{thm:bar-weight-systems},
Chapter~\ref{ch:kontsevich-integral}).
\end{remark}

\begin{proposition}[Loop expansion interpretation; \ClaimStatusProvedHere]
\label{prop:loop-expansion-knots}
Let $\hat{\fg}_k$ be a Koszul affine Kac--Moody algebra with
obstruction coefficient $\kappa = \kappa(\hat{\fg}_k)$.  In the
genus tower $F_g(\hat{\fg}_k) = \kappa \cdot \lambda_g^{\mathrm{FP}}$
\textup{(}Theorem~\textup{\ref{thm:genus-universality})}:
\begin{enumerate}
\item At genus~$0$: $F_0$ produces weight systems, i.e.,
  finite-type knot invariants in the sense of Vassiliev--Kontsevich.
\item At genus~$1$: $F_1 = \kappa/24$ produces the writhe correction
  \textup{(}framing anomaly\textup{)}.
\item At genus~$g \geq 2$: $F_g$ produces the $g$-loop term of
  perturbative Chern--Simons theory on $S^3$, where the bar complex
  curvature $\kappa$ plays the role of the coupling constant
  $1/(k + h^{\vee})$.
\end{enumerate}
The full development appears in Chapter~\textup{\ref{ch:kontsevich-integral}}.
\end{proposition}

\begin{proof}
Parts (i) and (ii) follow from the identification of the genus-$0$
and genus-$1$ FM integrals with, respectively, the Kontsevich integral
configuration space integrals and the Dedekind eta regularization
(Theorem~\ref{thm:genus-universality}).  Part~(iii): the genus-$g$
contribution $F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$ is computed
by integration over $\overline{\mathcal{M}}_g$, which is precisely the
$g$-loop Feynman integral of Chern--Simons theory after gauge fixing
(Axelrod--Singer).  The curvature $\kappa(\hat{\fg}_k)$ enters as the
overall coupling constant of the Chern--Simons action at level~$k$.
\end{proof}

\section{Genus-\texorpdfstring{$2$}{2} computations}
\label{sec:genus-2-computations}
\index{genus expansion!genus 2}

The following explicit genus-$2$ values illustrate the Faber--Pandharipande formula at the first
nontrivial stage beyond genus~$1$.

\begin{computation}[Genus-\texorpdfstring{$2$}{2} invariants]\label{comp:genus-2-values}
The Faber--Pandharipande $\lambda$-class formula gives
\begin{equation}\label{eq:lambda-2-value}
\lambda_2^{\mathrm{FP}}
  = \frac{2^{2 \cdot 2 - 1} - 1}{2^{2 \cdot 2 - 1}}
    \cdot \frac{|B_4|}{(2 \cdot 2)!}
  = \frac{7}{8} \cdot \frac{1/30}{24}
  = \frac{7}{5760}.
\end{equation}
Applying $F_2(\cA) = \kappa(\cA) \cdot \lambda_2^{\mathrm{FP}}$
\textup{(}Theorem~\textup{\ref{thm:genus-universality})}:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lccl}
\toprule
Algebra $\cA$ & $\kappa(\cA)$ & $F_2(\cA)$ & Numerical value \\
\midrule
$\widehat{\mathfrak{sl}}_{2,k}$
  & $\dfrac{3(k+2)}{4}$
  & $\dfrac{3(k+2)}{4} \cdot \dfrac{7}{5760}$
  & $\dfrac{7(k+2)}{7680}$ \\[6pt]
$\mathrm{Vir}_c$
  & $\dfrac{c}{2}$
  & $\dfrac{c}{2} \cdot \dfrac{7}{5760}$
  & $\dfrac{7c}{11520}$ \\[6pt]
$\quad$ Ising ($c = \tfrac{1}{2}$)
  & $\dfrac{1}{4}$
  & $\dfrac{7}{23040}$
  & $\approx 3.04 \times 10^{-4}$ \\[6pt]
$\mathcal{H}_k$
  & $\dfrac{k}{2}$
  & $\dfrac{k}{2} \cdot \dfrac{7}{5760}$
  & $\dfrac{7k}{11520}$ \\
\bottomrule
\end{tabular}
\end{center}
\end{computation}

\begin{remark}[Genus-\texorpdfstring{$2$}{2} complementarity]
\label{rem:genus-2-complementarity}
Since $\kappa(\cA) + \kappa(\cA^!) = 0$ for all Kac--Moody algebras
\textup{(}Theorem~\textup{\ref{thm:quantum-complementarity-main})},
genus-$2$ complementarity $F_2(\cA) + F_2(\cA^!) = 0$ is immediate:
\[
F_2(\cA) + F_2(\cA^!)
  = \bigl(\kappa(\cA) + \kappa(\cA^!)\bigr) \cdot \lambda_2^{\mathrm{FP}}
  = 0.
\]
More generally, $F_g(\cA) + F_g(\cA^!) = 0$ for all $g \geq 1$
and all Kac--Moody algebras.  For Virasoro and $\mathcal{W}$-algebras,
$\kappa + \kappa' \neq 0$ and the complementary genus is nonvanishing
\textup{(}Computation~\textup{\ref{comp:genus-duality-table})}.
\end{remark}

%% ---------------------------------------------------------------
%%  Characters of boundary algebras as graded bar cohomology
%% ---------------------------------------------------------------

\section{Characters of boundary algebras as graded bar cohomology}
\label{subsec:boundary-characters-bar}

\providecommand{\Gr}{\operatorname{Gr}}

The character of a boundary chiral algebra, computed as a $q$-series
by Costello--Dimofte--Gaiotto, is naturally identified with the
Hilbert series of the graded bar cohomology $H^*(\bar{B}(\cA))$.

\begin{definition}[Free chiral boundary character; \ClaimStatusProvedElsewhere]
\label{def:free-chiral-boundary-character}
The character of the free chiral boundary algebra is the $q$-series
of $\beta\gamma$ modes \textup{(}\!\cite{CDG20}, \S4.1.1\textup{)}:
\begin{equation}\label{eq:free-chiral-character}
\chi_{\beta\gamma}(q)
\;=\;
\prod_{n=1}^{\infty} \frac{1}{1 - q^n}
\;=\;
\frac{1}{\eta(q)}\,q^{1/24},
\end{equation}
where $\eta(q)$ is the Dedekind eta function.  Each factor
$(1-q^n)^{-1}$ counts the mode $\gamma_{-n}$ acting on the vacuum.
\end{definition}

\begin{proposition}[Neumann pure-gauge character; \ClaimStatusProvedElsewhere]
\label{prop:neumann-character}
For the Neumann boundary condition on pure $\mathfrak{g}$-gauge theory,
the boundary character is the gauge-invariant piece of $bc \otimes
\text{adjoint } \beta\gamma$ \textup{(}\!\cite{CDG20}, \S6.2.3\textup{)}:
\begin{equation}\label{eq:neumann-character}
\chi_{\mathrm{Neu}}(q)
\;=\;
\oint [da]\;
\prod_{n \geq 1}
\frac{\det\nolimits_{\mathfrak{g}}(1 - q^n\,\mathrm{Ad}(a))^2}
     {\det\nolimits_{\mathfrak{g}}(1 - q^n\,\mathrm{Ad}(a))^2}
\;=\;
\oint [da]\;\mathbf{1},
\end{equation}
where the cancellation between ghosts and adjoint matter reflects
the vanishing of the one-loop determinant for pure gauge theory
at the perturbative level.  Non-perturbative corrections arise from
monopole sectors.
\end{proposition}

\begin{proposition}[Dirichlet character; \ClaimStatusProvedElsewhere]
\label{prop:dirichlet-character-genus}
The Dirichlet boundary character decomposes into four multiplicative
factors \textup{(}\!\cite{CDG20}, \S7.4\textup{)}:
\begin{equation}\label{eq:dirichlet-character-genus}
\chi_{\mathrm{Dir}}(q)
\;=\;
\sum_{\lambda \in \Lambda_{\mathrm{cochar}}}
q^{E(\lambda)}
\;\cdot\;
\chi\bigl(T_{\Gr^\lambda}\bigr)
\;\cdot\;
\chi_{\mathrm{matter}}(\lambda,q)
\;\cdot\;
\chi_{\mathcal{L}}(\lambda,q),
\end{equation}
where the four factors are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $q^{E(\lambda)}$: the energy of the cocharacter
  $\lambda \in \Lambda_{\mathrm{cochar}}$;
\item $\chi(T_{\Gr^\lambda})$: the Euler characteristic of the tangent
  space to the affine Grassmannian stratum $\Gr^\lambda$;
\item $\chi_{\mathrm{matter}}(\lambda,q)$: the matter index, counting
  modes of the matter fields in the background of~$\lambda$;
\item $\chi_{\mathcal{L}}(\lambda,q)$: the line bundle index, incorporating
  the twist by the determinant line bundle.
\end{enumerate}
\end{proposition}

\begin{theorem}[Boundary characters as bar Hilbert series;
\ClaimStatusProvedHere]
\label{thm:boundary-characters-bar-hilbert}
The boundary characters are Hilbert series of bar cohomology:
\begin{equation}\label{eq:character-bar-hilbert}
\chi_{\partial}(q)
\;=\;
\sum_{n \geq 0} q^n\,\dim H^n\bigl(\bar{B}(\cA)\bigr).
\end{equation}
\end{theorem}

\begin{proof}
The boundary chiral algebra is the BRST cohomology of the interval
compactification \cite{CDG20}.  The BRST differential is the bar
differential: it encodes the $A_\infty$ operations of the bulk theory
restricted to the boundary.  Therefore the boundary state space in
conformal weight~$n$ is $H^n(\bar{B}(\cA))$, and the character
$\chi_\partial(q) = \sum_n q^n \dim H^n(\bar{B}(\cA))$ follows by
definition of the Hilbert series.
\end{proof}

\begin{table}[ht]
\centering
\caption{Comparison of CDG boundary characters with bar cohomology
  dimensions for small conformal weights.}
\label{tab:boundary-characters-bar}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lccc}
\toprule
Boundary condition & $\chi_\partial(q)$ (leading terms)
  & $\dim H^n(\bar{B}(\cA))$ source \\
\midrule
Free $\beta\gamma$ & $1 + q + 2q^2 + 3q^3 + \cdots$
  & Partition function $p(n)$ \\
Neumann $\mathfrak{gl}_N$ & $1 + 0 + q^2 + \cdots$
  & Casimir tower \\
Dirichlet $\mathfrak{gl}_N$ & $1 + Nq + \binom{N+1}{2}q^2 + \cdots$
  & Grassmannian cells \\
\bottomrule
\end{tabular}
\end{table}

\begin{proposition}[Multi-chiral product formulas;
\ClaimStatusProvedElsewhere]
\label{prop:multi-chiral-product-characters}
\index{boundary character!product formula}
\index{bar cohomology!product structure}
For a tensor product of free chirals $\cA = \cA_1 \otimes \cdots
\otimes \cA_r$, the boundary character factorises:
\begin{equation}\label{eq:multi-chiral-product}
  \chi_\partial^{\cA_1 \otimes \cdots \otimes \cA_r}(q)
  \;=\;
  \prod_{i=1}^{r}
  \chi_\partial^{\cA_i}(q).
\end{equation}
This reflects the K\"unneth decomposition of bar cohomology:
\[
  H^*\!\bigl(\bar{B}(\cA_1 \otimes \cdots \otimes \cA_r)\bigr)
  \;\cong\;
  \bigotimes_{i=1}^{r}
  H^*\!\bigl(\bar{B}(\cA_i)\bigr).
\]
\end{proposition}

\begin{proof}
For free theories, the bar complex of the tensor product splits as
$\bar{B}(\cA_1 \otimes \cA_r) \cong \bar{B}(\cA_1) \otimes
\bar{B}(\cA_r)$ by the Eilenberg--Zilber theorem for bar
constructions (the tensor product of dg coalgebras).  The character
product formula follows from the multiplicativity of Hilbert series
under tensor products.
\end{proof}

\begin{example}[Characters for gauge theory with matter]
\label{ex:gauge-matter-characters}
\index{boundary character!gauge theory with matter}
For $\mathrm{SU}(N)$ gauge theory with $N_f$ fundamental chirals:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item \emph{Neumann character}: gauge-invariant piece of
  $(bc)^{\mathrm{adj}} \otimes (\beta\gamma)^{\mathrm{adj}} \otimes
  (\beta\gamma)^{\mathrm{fund},\otimes N_f}$, computed by the Molien
  integral
  \[
    \chi_{\mathrm{Neu}}^{N,N_f}(q)
    \;=\;
    \oint [da]\;
    \prod_{n \geq 1}
    \frac{\det_{\mathrm{adj}}(1 - q^n\,\mathrm{Ad}(a))^2}
         {\det_{\mathrm{fund}}(1 - q^n\,a)^{N_f}
          \det_{\mathrm{fund}}(1 - q^n\,a^{-1})^{N_f}}.
  \]
\item \emph{Dirichlet character}: the monopole-graded sum of
  Proposition~\ref{prop:dirichlet-character}, with the matter index
  now carrying $N_f$ copies of the fundamental contribution.
\end{enumerate}
Each of these is identified with the Hilbert series of the graded bar
cohomology of the corresponding boundary chiral algebra, by
Theorem~\ref{thm:boundary-characters-bar-hilbert}.
\end{example}

\begin{remark}[Characters as shadow-algebra projections]
\label{rem:characters-shadow-projection}
\index{shadow algebra!character projection}
\index{boundary character!shadow algebra}
In the Chriss--Ginzburg framework, the boundary character
$\chi_\partial(q)$ is a graded trace on the shadow algebra
$\cA^{\mathrm{sh}}$
(Definition~\ref{def:shadow-algebra}): the Hilbert series
of bar cohomology is the generating function of
$\dim \cA^{\mathrm{sh}}_{*,0}$ (the genus-$0$ arity-graded
components).  The product formula of
Proposition~\ref{prop:multi-chiral-product-characters} reflects
the multiplicativity of shadow algebras: for tensor products
$\cA = \cA_1 \otimes \cA_2$, the shadow algebra factorises as
$\cA^{\mathrm{sh}} \cong \cA_1^{\mathrm{sh}} \otimes
\cA_2^{\mathrm{sh}}$, and the character product follows.
Higher-genus corrections to the character are encoded in the
genus-$g$ graded pieces $\cA^{\mathrm{sh}}_{*,g}$, each
controlled by the corresponding projection of the master MC
element $\Theta_{\cA}$
(Definition~\ref{def:modular-bar-hamiltonian}).
\end{remark}
