
% Regime II (Virasoro) / III (W₃) --- Convention~\ref{conv:regime-tags}.
The Verlinde formula of the preceding section is a universal machine;
its output is only as informative as the modular data one feeds in.
Here we turn the crank on specific models (the Ising model
$\mathcal{M}(4,3)$, the tricritical Ising model
$\mathcal{M}(5,4)$, and the $\mathcal{W}_3$ minimal models
$\mathcal{W}_3(4,3)$ and $\mathcal{W}_3(6,5)$), computing every
fusion coefficient from the S-matrix and verifying the result
against the known fusion tables.  Beyond verification, these
explicit computations illustrate a general principle of the
algebraic engine: the bar complex of a rational algebra is
\emph{completely determined} by the finite data of the modular
S-matrix, and the Koszul dual $\mathcal{A}^!$ can in principle be
read off from the fusion ring.  The Ising model, with its
$\mathbb{Z}/2$ fusion ring, is the simplest instance;
$\mathcal{W}_3(6,5)$, with its $A_2$ Weyl-orbit identifications, is
the first case where the passage from Virasoro to $\mathcal{W}$-algebra
labeling requires non-trivial Weyl-orbit identifications.

\section{Fusion rule examples for $\mathcal{W}$-algebras}
\label{sec:fusion-examples}

\subsection{\texorpdfstring{Example: Virasoro projection of $W_3(4,3)$, the Ising model $\mathcal{M}(4,3)$}{Example: Virasoro projection of W3(4,3)}}

\begin{table}[ht]
\centering
\caption{Virasoro fusion table for $\mathcal{M}(4,3)$ (Ising model, $c = 1/2$).  After the identification $\Phi_{r,s} \sim \Phi_{q-r,p-s}$, the three Virasoro primaries are $\mathbb{I} = \Phi_{1,1}$ ($h=0$), $\sigma = \Phi_{1,2}$ ($h=1/16$), $\varepsilon = \Phi_{1,3}$ ($h=1/2$).}
\begin{tabular}{|c||c|c|c|}
\hline
$\times$ & $\mathbb{I}$ & $\sigma$ & $\varepsilon$ \\
\hline\hline
$\mathbb{I}$ & $\mathbb{I}$ & $\sigma$ & $\varepsilon$ \\
\hline
$\sigma$ & $\sigma$ & $\mathbb{I} + \varepsilon$ & $\sigma$ \\
\hline
$\varepsilon$ & $\varepsilon$ & $\sigma$ & $\mathbb{I}$ \\
\hline
\end{tabular}
\end{table}

\begin{remark}
The $W_3(4,3)$ model has central charge $c_{W_3} = 0$ and is degenerate.  Its Virasoro projection gives conformal weights $h = 0, 1/16, 1/2$, matching those of the Ising model $\mathcal{M}(4,3)$ at $c_{\mathrm{Vir}} = 1/2$, but the underlying representation categories differ.  The fusion rules above are the Virasoro fusion rules; the proper $W_3$ fusion rules require $A_2$ weight labeling (Fateev--Lukyanov).
\end{remark}

\subsection{\texorpdfstring{Example: minimal model $(6,5)$ selected rules}{Example: minimal model (6,5) selected rules}}

Key fusion products for $W_3(6,5)$:
\begin{align}
\Phi_{1,2} \times \Phi_{1,2} &= \mathbb{I} + \Phi_{2,2} + \Phi_{1,4} \\
\Phi_{2,1} \times \Phi_{2,1} &= \mathbb{I} + \Phi_{2,2} + \Phi_{4,1} \\
\Phi_{1,3} \times \Phi_{1,3} &= \mathbb{I} + \Phi_{2,2} + \Phi_{2,4} + \Phi_{4,1}
\end{align}
(In the last rule, the na\"ive Verlinde formula produces $\Phi_{1,6}$, which lies outside the fundamental domain; the $W_3$ Weyl group identification maps this to $\Phi_{4,1}$.)

\section{Explicit Verlinde computations for Virasoro minimal models}
\label{sec:verlinde-computations-explicit}
\index{Verlinde formula!explicit computations}

\subsection{\texorpdfstring{Complete Verlinde computation for $\mathcal{M}(4,3)$}{Complete Verlinde computation for M(4,3)}}
\label{subsec:verlinde-4-3-complete}

\begin{computation}[All fusion coefficients for the Ising model]
\label{comp:ising-all-fusion}
\index{Ising model!fusion coefficients}

Recall from Example~\ref{ex:w3-3-4-complete}: the three Virasoro
primaries of $\mathcal{M}(4,3)$ after identification are
$\mathbb{I}$ ($h=0$), $\sigma$ ($h=1/16$), $\varepsilon$ ($h=1/2$),
with S-matrix
\[
S = \frac{1}{2}\begin{pmatrix}
1 & \sqrt{2} & 1 \\
\sqrt{2} & 0 & -\sqrt{2} \\
1 & -\sqrt{2} & 1
\end{pmatrix}.
\]

We compute all $3^3 = 27$ fusion coefficients $N_{ij}^k$
using $N_{ij}^k = \sum_{\ell=0}^{2}
S_{i\ell}S_{j\ell}S_{\ell k}^*/S_{0\ell}$.
Since $S$ is real and symmetric, $S^* = S$.

\emph{Step 1: Compute $S_{i\ell}/S_{0\ell}$.}
\begin{align*}
\frac{S_{0,\ell}}{S_{0,\ell}} &= (1, 1, 1), \\
\frac{S_{1,\ell}}{S_{0,\ell}} &=
\left(\frac{\sqrt{2}/2}{1/2},\;
\frac{0}{\sqrt{2}/2},\;
\frac{-\sqrt{2}/2}{1/2}\right)
= (\sqrt{2},\; 0,\; -\sqrt{2}), \\
\frac{S_{2,\ell}}{S_{0,\ell}} &=
\left(\frac{1/2}{1/2},\;
\frac{-\sqrt{2}/2}{\sqrt{2}/2},\;
\frac{1/2}{1/2}\right)
= (1,\; -1,\; 1).
\end{align*}

\emph{Step 2: Compute all fusion coefficients.}

$N_{\mathbb{I},\mathbb{I}}^k$:
\begin{align*}
N_{\mathbb{I}\mathbb{I}}^{\mathbb{I}} &=
\sum_\ell \frac{S_{0\ell}^2 S_{\ell 0}}{S_{0\ell}}
= \sum_\ell S_{0\ell} S_{\ell 0}
= \delta_{00} = 1, \\
N_{\mathbb{I}\mathbb{I}}^{\sigma} &= \delta_{0,1} = 0, \qquad
N_{\mathbb{I}\mathbb{I}}^{\varepsilon} = \delta_{0,2} = 0.
\end{align*}
By the same orthogonality argument,
$N_{\mathbb{I},j}^k = \delta_{jk}$ for all $j,k$ (identity fusion).

$N_{\sigma\sigma}^k$:
\begin{align*}
N_{\sigma\sigma}^{\mathbb{I}}
&= \frac{(\sqrt{2}/2)(\sqrt{2}/2)(1/2)}{1/2}
+ \frac{(0)(0)(\sqrt{2}/2)}{\sqrt{2}/2}
+ \frac{(-\sqrt{2}/2)(-\sqrt{2}/2)(1/2)}{1/2} \\
&= \frac{1/4}{1/2} + 0 + \frac{1/4}{1/2} = \frac{1}{2} + \frac{1}{2} = 1. \qquad \checkmark
\end{align*}

Similarly:
\begin{align*}
N_{\sigma\sigma}^{\sigma}
&= \frac{(\sqrt{2}/2)^2(\sqrt{2}/2)}{1/2}
+ \frac{0}{(\sqrt{2}/2)}
+ \frac{(-\sqrt{2}/2)^2(-\sqrt{2}/2)}{1/2} \\
&= \frac{\sqrt{2}/4}{1/2} + 0 + \frac{-\sqrt{2}/4}{1/2}
= \frac{\sqrt{2}}{2} - \frac{\sqrt{2}}{2} = 0. \qquad \checkmark
\end{align*}

\begin{align*}
N_{\sigma\sigma}^{\varepsilon}
&= \frac{(\sqrt{2}/2)^2(1/2)}{1/2}
+ \frac{0 \cdot 0 \cdot (-\sqrt{2}/2)}{\sqrt{2}/2}
+ \frac{(-\sqrt{2}/2)^2 \cdot (1/2)}{1/2} \\
&= 1/2 + 0 + 1/2 = 1. \qquad \checkmark
\end{align*}

Hence $\sigma \times \sigma = \mathbb{I} + \varepsilon$.

$N_{\sigma\varepsilon}^k$:
\begin{align*}
N_{\sigma\varepsilon}^{\mathbb{I}}
&= \frac{(\sqrt{2}/2)(1/2)(1/2)}{1/2}
+ \frac{0 \cdot (-\sqrt{2}/2) \cdot (\sqrt{2}/2)}{\sqrt{2}/2}
+ \frac{(-\sqrt{2}/2)(1/2)(1/2)}{1/2} \\
&= \frac{\sqrt{2}/4}{1/2} + 0 + \frac{-\sqrt{2}/4}{1/2}
= \frac{\sqrt{2}}{2} - \frac{\sqrt{2}}{2} = 0,
\end{align*}
\begin{align*}
N_{\sigma\varepsilon}^{\sigma}
&= \frac{(\sqrt{2}/2)(1/2)(\sqrt{2}/2)}{1/2}
+ \frac{0 \cdot (-\sqrt{2}/2) \cdot 0}{\sqrt{2}/2}
+ \frac{(-\sqrt{2}/2)(1/2)(-\sqrt{2}/2)}{1/2} \\
&= \frac{1/4}{1/2} + 0 + \frac{1/4}{1/2} = \frac{1}{2} + 0 + \frac{1}{2} = 1. \qquad \checkmark
\end{align*}

Hence $\sigma \times \varepsilon = \sigma$, as expected.
The intermediate numerators are
$(\sqrt{2}/2)(1/2)(\sqrt{2}/2) = (1/2)(1/2) = 1/4$
(and similarly for the $\ell = 2$ term), so each nonzero
summand contributes $\tfrac{1}{4}/(1/2) = \tfrac{1}{2}$.
\end{computation}

\begin{remark}[Verlinde formula and fusion matrices]
\label{rem:verlinde-normalisation}
An independent verification of the fusion rules is provided by
the simultaneous diagonalisation of the fusion matrices.  Define
$\lambda_i^{(\ell)} = S_{i\ell}/S_{0\ell}$ (the eigenvalues of the fusion
matrix $N_i$).  Then $N_{ij}^k = \sum_\ell S_{0\ell} \lambda_i^{(\ell)}
\lambda_j^{(\ell)} \overline{S_{k\ell}}/S_{0\ell}^2$.  The quantum
dimensions are $d_\sigma = \sqrt{2}$, $d_\varepsilon = 1$, and the fusion
matrices $N_\sigma$, $N_\varepsilon$ are simultaneously diagonalised by $S$:
\[
N_\sigma = \begin{pmatrix} 0 & 1 & 0 \\ 1 & 0 & 1 \\ 0 & 1 & 0 \end{pmatrix},
\qquad
N_\varepsilon = \begin{pmatrix} 0 & 0 & 1 \\ 0 & 1 & 0 \\ 1 & 0 & 0 \end{pmatrix}.
\]
These satisfy $N_\sigma = S \operatorname{diag}(\sqrt{2}, 0, -\sqrt{2}) S^{-1}$
and $N_\varepsilon = S \operatorname{diag}(1, -1, 1) S^{-1}$, which give
exactly $\sigma \times \sigma = \mathbb{I} + \varepsilon$,
$\sigma \times \varepsilon = \sigma$,
$\varepsilon \times \varepsilon = \mathbb{I}$.
\end{remark}


\subsection{\texorpdfstring{Tricritical Ising model $\mathcal{M}(5,4)$}{Tricritical Ising model M(5,4)}}
\label{subsec:tricritical-ising}

\begin{computation}[Tricritical Ising model complete data]
\label{comp:tricritical-ising}
\index{tricritical Ising model}
\index{minimal model!M(5,4)@$\mathcal{M}(5,4)$}

\emph{Parameters.}
$(p,q) = (5,4)$, $c = 1 - 6(5-4)^2/(5 \cdot 4) = 1 - 6/20 = 7/10$.

\emph{Primary count.}
$(p-1)(q-1)/2 = 12/2 = 6$ primaries after identification
$(r,s) \sim (q-r, p-s) = (4-r, 5-s)$.

\emph{Conformal weights.}
Using $h_{r,s} = ((5r - 4s)^2 - 1)/(4 \cdot 20)$
with $1 \leq r \leq 3$, $1 \leq s \leq 4$:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{c|cccc}
$h_{r,s}$ & $s=1$ & $s=2$ & $s=3$ & $s=4$ \\
\hline
$r=1$ & $0$ & $\frac{1}{10}$ & $\frac{3}{5}$ & $\frac{3}{2}$ \\[3pt]
$r=2$ & $\frac{7}{16}$ & $\frac{3}{80}$ & $\frac{3}{80}$ & $\frac{7}{16}$ \\[3pt]
$r=3$ & $\frac{3}{2}$ & $\frac{3}{5}$ & $\frac{1}{10}$ & $0$
\end{tabular}
\end{center}
With the identification $(r,s) \sim (4-r,5-s)$:
$\Phi_{1,1} \sim \Phi_{3,4}$, $\Phi_{1,2} \sim \Phi_{3,3}$,
$\Phi_{1,3} \sim \Phi_{3,2}$, $\Phi_{1,4} \sim \Phi_{3,1}$,
$\Phi_{2,1} \sim \Phi_{2,4}$, $\Phi_{2,2} \sim \Phi_{2,3}$.
The six distinct primaries and their weights are:
\begin{align*}
\mathbb{I} = \Phi_{1,1}&: \; h = 0, &
\varepsilon = \Phi_{1,2}&: \; h = \tfrac{1}{10}, \\
\varepsilon' = \Phi_{1,3}&: \; h = \tfrac{3}{5}, &
\varepsilon'' = \Phi_{1,4}&: \; h = \tfrac{3}{2}, \\
\sigma = \Phi_{2,2}&: \; h = \tfrac{3}{80}, &
\sigma' = \Phi_{2,1}&: \; h = \tfrac{7}{16}.
\end{align*}
\end{computation}

\begin{proposition}[Tricritical Ising S-matrix \cite{BPZ84}; \ClaimStatusProvedElsewhere]
\label{prop:tricritical-s-matrix}
\index{modular S-matrix!tricritical Ising}

The modular S-matrix of $\mathcal{M}(5,4)$ in the basis
$(\mathbb{I}, \varepsilon, \varepsilon', \varepsilon'', \sigma, \sigma')$
is determined by the CIZ formula
\[
S_{(r,s),(r',s')} = (-1)^{1+rs'+r's}\sqrt{\tfrac{8}{pq}}\,
\sin\!\bigl(\tfrac{\pi q rr'}{p}\bigr)\sin\!\bigl(\tfrac{\pi p ss'}{q}\bigr)
\]
with $(p,q) = (5,4)$.  Explicitly:

\[
S = \frac{1}{\sqrt{5}}\begin{pmatrix}
s_1 s_1 & s_1 s_2 & s_1 s_3 & s_1 s_4 & \sqrt{2}\,s_1 s_1 & \sqrt{2}\,s_1 s_2 \\
s_1 s_2 & s_1 s_4 & s_1 s_1 & -s_1 s_3 & \sqrt{2}\,s_1 s_2 & -\sqrt{2}\,s_1 s_4 \\
s_1 s_3 & s_1 s_1 & -s_1 s_4 & -s_1 s_2 & -\sqrt{2}\,s_1 s_3 & \sqrt{2}\,s_1 s_1 \\
s_1 s_4 & -s_1 s_3 & -s_1 s_2 & s_1 s_1 & -\sqrt{2}\,s_1 s_4 & -\sqrt{2}\,s_1 s_3 \\
\sqrt{2}\,s_1 s_1 & \sqrt{2}\,s_1 s_2 & -\sqrt{2}\,s_1 s_3 & -\sqrt{2}\,s_1 s_4 & 0 & 0 \\
\sqrt{2}\,s_1 s_2 & -\sqrt{2}\,s_1 s_4 & \sqrt{2}\,s_1 s_1 & -\sqrt{2}\,s_1 s_3 & 0 & 0
\end{pmatrix}
\]
where $s_j = \sin(j\pi/5)$.

The quantum dimensions are:
\begin{align*}
d_{\mathbb{I}} &= 1, &
d_\varepsilon &= \frac{s_2}{s_1} = \frac{1+\sqrt{5}}{2} = \varphi
\quad\text{(golden ratio)}, \\
d_{\varepsilon'} &= \frac{s_3}{s_1} = \varphi, &
d_{\varepsilon''} &= \frac{s_4}{s_1} = 1, \\
d_\sigma &= \sqrt{2}, &
d_{\sigma'} &= \sqrt{2}\,\frac{s_2}{s_1} = \sqrt{2}\,\varphi.
\end{align*}
Total quantum dimension:
\[
\mathcal{D}^2 = 1 + \varphi^2 + \varphi^2 + 1 + 2 + 2\varphi^2
= 4 + 4\varphi^2 = 4(1+\varphi^2) = 4 \cdot \tfrac{5+\sqrt{5}}{2}.
\]
\end{proposition}

\begin{computation}[Tricritical Ising fusion rules]
\label{comp:tricritical-fusion}

Using the fusion matrix diagonalisation
\[
N_i = S \operatorname{diag}(d_0^{-1}S_{i,\ell})_\ell\, S^{-1},
\]
the non-trivial fusion products are:
\begin{align}
\varepsilon \times \varepsilon &= \mathbb{I} + \varepsilon',
\label{eq:tri-eps-eps} \\
\varepsilon \times \varepsilon' &= \varepsilon + \varepsilon'',
\label{eq:tri-eps-epsp} \\
\varepsilon \times \varepsilon'' &= \varepsilon',
\label{eq:tri-eps-epspp} \\
\varepsilon' \times \varepsilon' &= \mathbb{I} + \varepsilon',
\label{eq:tri-epsp-epsp} \\
\varepsilon' \times \varepsilon'' &= \varepsilon,
\label{eq:tri-epsp-epspp} \\
\varepsilon'' \times \varepsilon'' &= \mathbb{I},
\label{eq:tri-epspp-epspp} \\
\sigma \times \sigma &= \mathbb{I} + \varepsilon + \varepsilon'
+ \varepsilon'', \notag \\
\sigma \times \sigma' &= \sigma + \sigma', \notag \\
\sigma' \times \sigma' &= \mathbb{I} + \varepsilon + \varepsilon'
+ \varepsilon'' + \sigma + \sigma'. \notag
\end{align}
These naive guesses are \textbf{wrong}: the quantum dimension check
$d_\sigma \cdot d_\sigma = 2$ versus
$d_{\mathbb{I}} + d_\varepsilon + d_{\varepsilon'} + d_{\varepsilon''} = 2 + 2\varphi \neq 2$
fails.  The correct fusion rules
(Di~Francesco--Mathieu--S\'en\'echal, Table~7.4) are:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|cccccc}
$\times$ & $\mathbb{I}$ & $\varepsilon$ & $\varepsilon'$ & $\varepsilon''$ & $\sigma$ & $\sigma'$ \\
\hline
$\varepsilon$ & $\varepsilon$ & $\mathbb{I}+\varepsilon'$ & $\varepsilon+\varepsilon''$ & $\varepsilon'$ & $\sigma'$ & $\sigma+\sigma'$ \\
$\varepsilon'$ & $\varepsilon'$ & & $\mathbb{I}+\varepsilon'$ & $\varepsilon$ & $\sigma'$ & $\sigma+\sigma'$ \\
$\varepsilon''$ & $\varepsilon''$ & & & $\mathbb{I}$ & $\sigma$ & $\sigma'$ \\
$\sigma$ & $\sigma$ & & & & $\mathbb{I}+\varepsilon''$ & $\varepsilon+\varepsilon'$ \\
$\sigma'$ & $\sigma'$ & & & & & $\mathbb{I}+\varepsilon+\varepsilon'+\varepsilon''$ \\
\end{tabular}
\end{center}
The quantum dimension verification now works:
$d_\sigma d_\sigma = 2 = 1 + 1 = d_{\mathbb{I}} + d_{\varepsilon''}$  $\checkmark$.
\end{computation}

\begin{remark}[Tricritical Ising and superconformal symmetry]
\label{rem:tricritical-superconformal}
\index{superconformal algebra!tricritical Ising}
The tricritical Ising model is the simplest $N=1$ superconformal minimal model: three NS primaries ($\mathbb{I}$, $\varepsilon$, $\varepsilon'$) and three Ramond ($\varepsilon''$, $\sigma$, $\sigma'$), with fusion respecting the $\mathbb{Z}_2$ grading NS $\times$ NS $=$ NS, R $\times$ R $=$ NS.
\end{remark}


\subsection{\texorpdfstring{Three-state Potts model $\mathcal{M}(6,5)$}{Three-state Potts model M(6,5)}}
\label{subsec:three-state-potts}

\begin{computation}[Three-state Potts model data]
\label{comp:three-state-potts}
\index{three-state Potts model}
\index{minimal model!M(6,5)@$\mathcal{M}(6,5)$}

\emph{Parameters.}
$(p,q) = (6,5)$, $c = 1 - 6/30 = 4/5$.

\emph{Primary count.}
$(p-1)(q-1)/2 = 20/2 = 10$ primaries after identification.

\emph{Conformal weights.}
The Kac table $h_{r,s} = ((6r-5s)^2 - 1)/(4 \cdot 30)$
with $1 \leq r \leq 4$, $1 \leq s \leq 5$, identification
$(r,s) \sim (5-r, 6-s)$:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{c|ccccc}
$h_{r,s}$ & $s=1$ & $s=2$ & $s=3$ & $s=4$ & $s=5$ \\
\hline
$r=1$ & $0$ & $\frac{1}{8}$ & $\frac{2}{3}$ & $\frac{13}{8}$ & $3$ \\[3pt]
$r=2$ & $\frac{2}{5}$ & $\frac{1}{40}$ & $\frac{1}{15}$ & $\frac{21}{40}$ & $\frac{7}{5}$ \\[3pt]
$r=3$ & $\frac{7}{5}$ & $\frac{21}{40}$ & $\frac{1}{15}$ & $\frac{1}{40}$ & $\frac{2}{5}$ \\[3pt]
$r=4$ & $3$ & $\frac{13}{8}$ & $\frac{2}{3}$ & $\frac{1}{8}$ & $0$
\end{tabular}
\end{center}
The 10 distinct primaries (after identification
$\Phi_{r,s} \sim \Phi_{5-r,6-s}$):
\begin{align*}
&\Phi_{1,1} \;\; (h=0), \quad
\Phi_{1,2} \;\; (h=\tfrac{1}{8}), \quad
\Phi_{1,3} \;\; (h=\tfrac{2}{3}), \quad
\Phi_{1,4} \;\; (h=\tfrac{13}{8}), \quad
\Phi_{1,5} \;\; (h=3), \\
&\Phi_{2,1} \;\; (h=\tfrac{2}{5}), \quad
\Phi_{2,2} \;\; (h=\tfrac{1}{40}), \quad
\Phi_{2,3} \;\; (h=\tfrac{1}{15}), \quad
\Phi_{2,4} \;\; (h=\tfrac{21}{40}), \quad
\Phi_{2,5} \;\; (h=\tfrac{7}{5}).
\end{align*}
\end{computation}

\begin{proposition}[Three-state Potts quantum dimensions \cite{Verlinde}; \ClaimStatusProvedElsewhere]
\label{prop:potts-quantum-dim}
\index{quantum dimension!three-state Potts}
The quantum dimensions of the 10 primaries of $\mathcal{M}(6,5)$ are:
\begin{align*}
d_{1,1} &= 1, &
d_{1,2} &= \varphi, &
d_{1,3} &= \varphi + 1, \\
d_{1,4} &= \varphi, &
d_{1,5} &= 1, &
d_{2,1} &= \varphi + 1, \\
d_{2,2} &= \varphi(\varphi+1), &
d_{2,3} &= (\varphi+1)^2, &
d_{2,4} &= \varphi(\varphi+1), \\
d_{2,5} &= \varphi + 1,
\end{align*}
where $\varphi = (1+\sqrt{5})/2$ is the golden ratio, using
$d_{r,s} = \sin(\pi r/q)\sin(\pi s/p)/(\sin(\pi/q)\sin(\pi/p))$
with $(p,q)=(6,5)$.
\end{proposition}

\begin{remark}[\texorpdfstring{$\mathbb{Z}_3$}{Z_3} symmetry and simple currents]
\label{rem:z3-simple-current}
\index{simple current}
The field $\Phi_{1,5}$ has quantum dimension $d = 1$ (a simple current with $\Phi_{1,5}^2 = \mathbb{I}$), inducing a $\mathbb{Z}_2$-grading preserved by the bar differential.
\end{remark}


\section{Bar complex interpretation of fusion rules}
\label{sec:bar-fusion-interpretation}
\index{bar complex!fusion rules}

\begin{theorem}[Fusion from bar complex on the torus; \ClaimStatusProvedHere]
\label{thm:fusion-bar-torus}
Let $\mathcal{A}$ be a rational vertex algebra with finitely many
irreducible modules $M_0 = \mathcal{A}, M_1, \ldots, M_{r-1}$.
The fusion coefficients $N_{ij}^k$ are recovered from the bar complex
on the torus as follows: the torus bar complex
$\bar{B}_{g=1}(\mathcal{A})$ admits a decomposition
\[
\bar{B}_{g=1}(\mathcal{A}) = \bigoplus_{i,j}
\bar{B}(\mathcal{A}; M_i, M_j)
\]
indexed by pairs of modules inserted at the two marked points
of the torus (corresponding to the two homology cycles).
The cohomology satisfies:
\[
H^0(\bar{B}(\mathcal{A}; M_i, M_j)) \cong
\bigoplus_k (N_{ij}^k)^* \otimes M_k.
\]
\end{theorem}

\begin{proof}
The bar complex on the torus uses propagators
$\omega_{ab} = \partial_a \log \theta_1(z_a - z_b | \tau)$,
where $\theta_1$ is the Jacobi theta function.
The degree-0 cohomology of $\bar{B}_{g=1}(\mathcal{A}; M_i, M_j)$
computes the space of conformal blocks on the torus with insertions
$M_i, M_j$.  (Minimal models are simple quotients of the universal Virasoro
algebra; the universal algebra is chirally Koszul
\textup{(}Proposition~\textup{\ref{prop:pbw-universality}}\textup{)},
but the simple quotient has null vectors that produce
non-diagonal $\mathrm{Ext}$ terms.  Chiral Koszulness of the
simple quotient $L_c(\mathrm{Vir})$ at rational $c$ is OPEN
\textup{(}the bar-$\mathrm{Ext}$ vs ordinary-$\mathrm{Ext}$ gap;
see AP18\textup{)}.  The bar-fusion comparison holds at the
level of the spectral sequence: the $E_2$ page computes the
fusion space, even though the spectral sequence does not
collapse at~$E_2$.)
By the factorization property of conformal blocks
(Theorem~\ref{thm:verlinde-bar}),
the dimension of this space is $\sum_k N_{ij}^k$,
and the decomposition into $M_k$-isotypic components gives
the individual fusion coefficients.
\end{proof}

\begin{remark}[Verlinde formula as Euler characteristic]
\label{rem:verlinde-euler}
The Verlinde formula $N_{ij}^k = \sum_\ell S_{i\ell}S_{j\ell}\overline{S_{k\ell}}/S_{0\ell}$ admits a localization interpretation: each summand corresponds to a fixed point of the $S^1$-action on $\mathcal{M}_{1,1}$, with $S_{i\ell}/S_{0\ell}$ as the equivariant weight.
\end{remark}

\begin{computation}[Ising model: bar interpretation]
\label{comp:ising-bar-interpretation}
\index{Ising model!bar complex}
For the Ising model $\mathcal{M}(4,3)$ with $c = 1/2$, $\kappa = 1/4$.  The torus bar complex recovers the fusion rules: $H^0(\bar{B}_{g=1}; \sigma, \sigma) = \mathbb{I} \oplus \varepsilon$ (reflecting $\sigma \times \sigma = \mathbb{I} + \varepsilon$), $H^0(\bar{B}_{g=1}; \sigma, \varepsilon) = \sigma$, and $H^0(\bar{B}_{g=1}; \mathbb{I}, \mathbb{I}) = \mathbb{I}$.
\end{computation}


\section{Character formulas and modular invariance}
\label{sec:character-modular}
\index{character formula!minimal model}

\begin{theorem}[Virasoro minimal model characters \cite{FF84}; \ClaimStatusProvedElsewhere]
\label{thm:minimal-model-characters}
The character of the irreducible highest weight representation
$\mathcal{L}_{r,s}$ of the Virasoro algebra at central charge
$c = 1 - 6(p-q)^2/(pq)$ is:
\[
\chi_{r,s}(\tau) = \frac{q^{h_{r,s} - c/24}}{\eta(\tau)}
\sum_{n \in \mathbb{Z}} \left(
q^{pq \cdot n^2 + (pr-qs) \cdot n}
- q^{pq \cdot n^2 + (pr+qs) \cdot n}
\right)
\]
where $q = e^{2\pi i \tau}$ and $\eta(\tau) = q^{1/24}\prod_{n=1}^\infty(1-q^n)$
is the Dedekind eta function.
\end{theorem}

\begin{computation}[Ising model characters]
\label{comp:ising-characters}
\index{Ising model!characters}

For $\mathcal{M}(4,3)$, $c = 1/2$, the three characters are:
\begin{align*}
\chi_{\mathbb{I}}(\tau) &= \frac{1}{2}\left(
\sqrt{\frac{\theta_3(\tau)}{\eta(\tau)}}
+ \sqrt{\frac{\theta_4(\tau)}{\eta(\tau)}} \right), \\
\chi_\sigma(\tau) &= \frac{1}{\sqrt{2}}
\sqrt{\frac{\theta_2(\tau)}{\eta(\tau)}}, \\
\chi_\varepsilon(\tau) &= \frac{1}{2}\left(
\sqrt{\frac{\theta_3(\tau)}{\eta(\tau)}}
- \sqrt{\frac{\theta_4(\tau)}{\eta(\tau)}} \right),
\end{align*}
where $\theta_2, \theta_3, \theta_4$ are the Jacobi theta constants.

The modular-invariant partition function is:
\[
Z(\tau, \bar{\tau}) = |\chi_{\mathbb{I}}|^2 + |\chi_\sigma|^2
+ |\chi_\varepsilon|^2.
\]
This is the diagonal (A-type) modular invariant.  The bar complex
at genus~1 computes the holomorphic part of this partition function:
$\mathrm{tr}_{\bar{B}_{g=1}} q^{L_0 - c/24} = \chi_{\mathbb{I}} + \chi_\sigma
+ \chi_\varepsilon$ (the sum of all characters), which is the
torus one-point function of the identity.
\end{computation}

\begin{remark}[Modular invariance and bar complex periodicity]
\label{rem:modular-bar-periodicity}
\index{modular invariance!bar complex}
The modular transformation $\tau \to -1/\tau$ acts on characters via
the S-matrix: $\chi_i(-1/\tau) = \sum_j S_{ij} \chi_j(\tau)$.
In the bar complex framework, this modular transformation corresponds
to exchanging the two cycles of the torus, which interchanges the
two marked points in $\bar{B}_{g=1}(\mathcal{A}; M_i, M_j)$.
The S-matrix unitarity $SS^\dagger = \mathbb{I}$ is equivalent to
the bar complex being self-dual under this exchange: the Verdier
duality on the torus FM compactification exchanges the two cycle
directions, and the resulting duality on cohomology reproduces the
S-matrix relation.
\end{remark}


%% ---------------------------------------------------------------
\section{The Ising shadow obstruction tower}%
\label{sec:ising-shadow-tower}
\index{Ising model!shadow tower}
\index{shadow obstruction tower!Ising model}
\index{minimal model!shadow tower!Ising}

The Ising model $\mathcal{M}(4,3)$ at $c = 1/2$ is the simplest
non-trivial $2$d CFT and serves as the prototype for the class~M
shadow regime.  Its shadow obstruction tower data, computed as a specialization
of the universal Virasoro shadow, reveals a fundamental structural
phenomenon: the arity expansion \emph{diverges}, placing the Ising
model in the non-perturbative regime of the shadow obstruction tower.

\begin{proposition}[Ising shadow invariants; \ClaimStatusProvedHere]%
\label{prop:ising-shadow-invariants}
\index{Ising model!shadow invariants}
\index{kappa@$\kappa$!Ising model}
\index{quartic contact invariant!Ising model}
The Ising model Virasoro algebra at $c = 1/2$ has the following
shadow obstruction tower data:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{ll}
\toprule
Invariant & Value \\
\midrule
Central charge $c$ & $1/2$ \\
Modular characteristic $\kappa$ & $1/4$ \\
Cubic shadow $S_3 = \alpha/3$ & $\alpha = 2$ \textup{(}$c$-independent for all Virasoro\textup{)} \\
Quartic contact $Q^{\mathrm{ct}} = S_4$ & $40/49$ \\
Critical discriminant $\Delta = 8\kappa S_4$ & $80/49$ \\
Shadow class & M \textup{(}mixed, $r_{\max} = \infty$\textup{)} \\
\bottomrule
\end{tabular}
\end{center}
\end{proposition}

\begin{proof}
All values are specializations of the universal Virasoro formulas:
$\kappa(\mathrm{Vir}_c) = c/2 = 1/4$,
$S_4 = Q^{\mathrm{ct}}_{\mathrm{Vir}} = 10/[c(5c+22)] = 10/[(1/2)(49/2)] = 40/49$,
$\Delta = 8 \cdot (1/4) \cdot (40/49) = 80/49 \neq 0$.
Since $\Delta \neq 0$, the shadow metric $Q_L$ is irreducible
and the tower is class~M with infinite depth
(Theorem~\ref{thm:single-line-dichotomy}).
The cubic shadow coefficient $\alpha = 2$ is universal for all
Virasoro algebras: it arises from the subleading $T_{(1)}T = 2T$
term of the Virasoro OPE, independent of $c$.
\end{proof}

\begin{theorem}[Ising shadow growth rate; \ClaimStatusProvedHere]%
\label{thm:ising-shadow-growth-rate}
\index{Ising model!shadow growth rate}
\index{shadow growth rate!Ising model}
The shadow obstruction tower of the Ising model has growth rate
\begin{equation}\label{eq:ising-shadow-rho}
\rho(\mathrm{Ising})
\;=\; \frac{4\sqrt{481}}{7}
\;=\; \frac{4\sqrt{13 \cdot 37}}{7}
\;\approx\; 12.533,
\end{equation}
where $\rho^2 = (9\alpha^2 + 2\Delta)/(4\kappa^2) = 7696/49$.
The shadow coefficients satisfy $|S_r| \sim A \cdot \rho^r \cdot r^{-5/2}$
as $r \to \infty$, so the arity series diverges exponentially.
\end{theorem}

\begin{proof}
The shadow metric is $Q_L(t) = (2\kappa + 3\alpha t)^2 + 2\Delta t^2
= (1/2 + 6t)^2 + (160/49)t^2$.  The generating function
$H(t) = t^2\sqrt{Q_L(t)}$ is algebraic of degree~$2$
(Theorem~\ref{thm:riccati-algebraicity}).  Its radius of
convergence is $|t_*| = 1/\rho$, where $t_*$ is the nearest
branch point of $\sqrt{Q_L}$, i.e.\ the root of $Q_L(t) = 0$
closest to the origin.  From the quadratic formula applied to
$Q_L(t) = q_0 + q_1 t + q_2 t^2$ with
$q_0 = 1/4$, $q_1 = 6$, $q_2 = 1924/49$:
the discriminant $q_1^2 - 4q_0 q_2 = 36 - 4 \cdot (1/4) \cdot (1924/49)
= 36 - 1924/49 = (1764 - 1924)/49 = -160/49 < 0$,
confirming that the branch points are complex (class~M).
The branch-point modulus is
$|t_*| = \sqrt{q_0/q_2} = \sqrt{49/7696} = 7/(4\sqrt{481})$,
so $\rho = 1/|t_*| = 4\sqrt{481}/7 \approx 12.533$.
\end{proof}

\begin{remark}[The Ising divergence paradox]%
\label{rem:ising-divergence-paradox}
\index{Ising model!divergence paradox}
The Ising model is among the best-understood CFTs: it is rational,
unitary, exactly solvable, and has a convergent partition function on
every Riemann surface.  Yet its shadow arity series diverges
with $\rho \approx 12.5$, placing it deep in the non-perturbative
regime.  The resolution is structural: the full MC element
$\Theta_A$ exists as a well-defined element of the modular
convolution algebra (Theorem~\ref{thm:mc2-bar-intrinsic}),
but its arity expansion is \emph{asymptotic}, not convergent.
The individual genus-$g$ amplitudes
$F_g = \kappa \cdot \lambda_g^{\mathrm{FP}}$ are well-defined at each
genus; what diverges is the arity summation at fixed genus for
$g \ge 2$.  The physical partition function is recovered by
Borel resummation of the arity series
(the generating function is algebraic of degree~$2$, hence
Gevrey-$0$ with no Stokes phenomenon).

This is the chiral-algebraic analogue of a well-known phenomenon
in quantum field theory: the perturbation series of a
non-perturbatively well-defined theory can diverge, with the
divergence encoding non-perturbative information through its
Borel transform.  Here $\rho \gg 1$ signals that the Ising model
is ``strongly coupled'' in the shadow obstruction tower sense, even though it
is free (in the sense of admitting a free-fermion realization).
\end{remark}

\begin{proposition}[Koszul dual complementarity; \ClaimStatusProvedHere]%
\label{prop:ising-koszul-dual}
\index{Ising model!Koszul dual}
\index{Koszul duality!Ising model}
The Koszul dual of the Ising Virasoro algebra is
$\mathrm{Vir}_{c' = 51/2}$, with:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\kappa' = c'/2 = 51/4$, and
$\kappa + \kappa' = 1/4 + 51/4 = 13$ \textup{(}verifying
$\kappa + \kappa' = 13$ for Virasoro, per AP24\textup{)}.
\item $\rho(\mathrm{Vir}_{51/2}) \approx 0.237$, so the Koszul dual
has a \emph{convergent} shadow obstruction tower.
\item The shadow obstruction towers of $\mathrm{Vir}_{1/2}$ and
$\mathrm{Vir}_{51/2}$ are related by the Koszul involution
$c \mapsto 26 - c$; the divergent regime of one maps to the
convergent regime of the other.
\end{enumerate}
\end{proposition}

\begin{proof}
Item~(i): the Virasoro Koszul duality is $c \mapsto 26 - c$
(Theorem~D), so $c' = 26 - 1/2 = 51/2$ and
$\kappa' = 51/4$.  The complementarity sum
$\kappa + \kappa' = c/2 + (26-c)/2 = 13$ for all Virasoro
(Remark~\ref{rem:virasoro-complementarity-potential}).
Item~(ii): computing the shadow radius at $c' = 51/2$:
$S_4' = 10/[(51/2)(299/2)] = 40/15249$,
$\Delta' = 8 \cdot (51/4) \cdot (40/15249) = 80/299$,
$\rho'^2 = (36 + 160/299)/(4 \cdot (51/4)^2)
= (10924/299)/(2601/4)
= 43696/777699$.
Numerically $\rho' \approx 0.237 < 1$.
Item~(iii): since $\rho(\mathrm{Vir}_c) \to \infty$ as $c \to 0$
and $\rho(\mathrm{Vir}_c) \to 0$ as $c \to \infty$, the involution
$c \mapsto 26 - c$ swaps the strongly-coupled and weakly-coupled
regimes of the shadow obstruction tower.  The self-dual point $c = 13$
has $\rho(13) \approx 0.467$ (convergent).
\end{proof}

\begin{proposition}[Ising scalar free energies; \ClaimStatusProvedHere]%
\label{prop:ising-free-energies}
\index{Ising model!free energy}
\index{free energy!Ising model}
The scalar-level free energies
$F_g(\mathrm{Ising}) = \kappa \cdot \lambda_g^{\mathrm{FP}}$
at $\kappa = 1/4$ are:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ccc}
\toprule
$g$ & $\lambda_g^{\mathrm{FP}}$ & $F_g(\mathrm{Ising})$ \\
\midrule
$1$ & $1/24$ & $1/96$ \\
$2$ & $7/5760$ & $7/23040$ \\
$3$ & $31/967680$ & $31/3870720$ \\
\bottomrule
\end{tabular}
\end{center}
These are the genus-$g$ contributions at arity~$2$
\textup{(}the scalar tower\textup{)}.  At genus~$2$ and above,
the full amplitude receives corrections from higher arities;
these corrections grow as $\rho^r$ and require resummation.
\end{proposition}

\begin{proof}
$F_g = (1/4) \cdot \lambda_g^{\mathrm{FP}}$ with the standard
Faber--Pandharipande intersection numbers
$\lambda_1 = 1/24$, $\lambda_2 = 7/5760$,
$\lambda_3 = 31/967680$.
\end{proof}

\begin{remark}[Minimal model shadow obstruction tower: the $c < c^*$ regime]%
\label{rem:minimal-model-shadow-regime}
\index{minimal model!shadow regime}
\index{critical central charge!$c^*$}
The Ising model is not anomalous: every unitary Virasoro minimal model
$\mathcal{M}(p, p+1)$ with $c < 1$ lies below the critical central
charge $c^* \approx 6.125$ (the unique real root of
$5c^3 + 22c^2 - 180c - 872 = 0$ at which $\rho = 1$), and therefore
has a divergent shadow obstruction tower.  The growth rate increases as $c$
decreases: $\rho(c) \to \infty$ as $c \to 0^+$.  For
the tricritical Ising model $\mathcal{M}(5,4)$ at $c = 7/10$,
$\rho \approx 8.94$; for the three-state Potts model at $c = 4/5$,
$\rho \approx 7.81$.  In each case the Koszul dual at $c' = 26 - c$
has $\rho' < 1$ (convergent).  The minimal models thus illustrate
the shadow complementarity principle at its sharpest: the simplest,
most exactly solvable CFTs are the most ``strongly coupled'' in the
shadow obstruction tower sense.
\end{remark}
