% ======================================================================
% Chapter: Symmetric Orbifolds
% ======================================================================

\chapter{\texorpdfstring{The symmetric orbifold $\operatorname{Sym}^N(X)$}{The symmetric orbifold Sym\^{}N(X)}}\label{chap:symmetric-orbifold}
% Regime III: non-perturbative (Convention~\ref{conv:regime-tags}).

The notation $\operatorname{Sym}^N(X)$ carries three different
objects. The fixed-point chiral algebra is
\[
 X_N^{\mathrm{id}} := (X^{\otimes N})^{S_N};
\]
its ordered bar complex is built from the invariant chiral product.
The full permutation-orbifold conformal field theory has state space
\[
 \mathcal H_N^{\mathrm{orb}}
 = \bigoplus_{[\sigma]\in \operatorname{Conj}(S_N)}
 \mathcal H_\sigma^{C(\sigma)} ,
\]
with $C(\sigma)$ the centralizer and with twisted sectors indexed by
conjugacy classes. A
$G$-crossed orbifold completion, when constructed, adjoins twist
fields as genuine fields and has a different bar complex. The
genus-$1$ scalar identity
\[
 \kappa^{\mathrm{id}}_1(X_N^{\mathrm{id}})
 = N\,\kappa(X)
\]
belongs only to the first object: the identity-sector fixed-point
chiral algebra. The DMVV product \cite{DMVV97} computes the
genus-$1$ elliptic genera of the second object; it does not compute
ordered chiral bar cohomology.

The diagonal fields
$a_\Delta=\sum_{i=1}^N a^{(i)}\in (X^{\otimes N})^{S_N}$ retain the
pole orders of the seed OPE, while scalar residues add over the
$N$ independent copies. Twisted sectors have conformal weights
\[
 h_{\mathrm{twist}}(\lambda)
 = \frac{c(X)}{24}\sum_j m_j\Bigl(j-\frac1j\Bigr)
\]
for cycle type $\lambda=(1^{m_1}2^{m_2}\cdots)$, and they affect the
full orbifold partition function. They are not generators of the
ordered bar complex of $X_N^{\mathrm{id}}$.

\begin{definition}[The averaging kernel of the fixed-point bar]
\label{def:symn-averaging-kernel}
Two finite groups act in this chapter. The group $S_N$ permutes the
$N$ tensor factors of $X^{\otimes N}$. The group $\Sigma_r$ permutes
the $r$ ordered inputs in bar degree~$r$ of
\[
 \barB^{\mathrm{ord}}_r(X_N^{\mathrm{id}})
 =
 (s^{-1}\overline{X_N^{\mathrm{id}}})^{\otimes r}.
\]
Over characteristic zero the ordered-to-symmetric averaging map in
bar degree~$r$ is the Reynolds projector
\[
 \operatorname{av}_{r,N}
 =
 \frac{1}{r!}\sum_{\tau\in\Sigma_r}\tau
 \colon
 \barB^{\mathrm{ord}}_r(X_N^{\mathrm{id}})
 \longrightarrow
 \bigl(\barB^{\mathrm{ord}}_r(X_N^{\mathrm{id}})\bigr)^{\Sigma_r}.
\]
Its kernel
\[
 \mathcal K^{\mathrm{av}}_{r,N}(X)
 :=
 \ker(\operatorname{av}_{r,N})
\]
is the lost ordered information. In the weight-completed finite-type
setting the same notation denotes the closed kernel of the continuous
Reynolds projector on
$\widehat{\barB}^{\mathrm{ord}}_r(X_N^{\mathrm{id}})$.
\end{definition}

\begin{proposition}[Ordered data and symmetric shadow;
\ClaimStatusProvedHere]\label{prop:symn-averaging-kernel}
\index{symmetric orbifold!averaging kernel}
Assume each graded piece of $X_N^{\mathrm{id}}$ is finite-dimensional,
or work in the weight-completed product topology. Then, as a graded
vector space,
\[
 \barB^{\mathrm{ord}}_r(X_N^{\mathrm{id}})
 =
 \bigl(\barB^{\mathrm{ord}}_r(X_N^{\mathrm{id}})\bigr)^{\Sigma_r}
 \oplus \mathcal K^{\mathrm{av}}_{r,N}(X).
\]
The first summand is the symmetric/coinvariant shadow of the ordered
bar data; the second summand is invisible to the symmetric shadow.
This is not a decomposition of bar complexes unless the bar
differential preserves the two summands.
\end{proposition}

\begin{proof}
The representation category of the finite group $\Sigma_r$ over
characteristic zero is semisimple. The Reynolds operator
$\operatorname{av}_{r,N}$ is an idempotent whose image is the trivial
$\Sigma_r$-isotypic component and whose kernel is the direct sum of
the nontrivial isotypic components. Passing to finite weight windows
and then to the completed inverse product gives the completed
statement. The warning about the differential is the
non-splitting phenomenon for the ordered-to-symmetric map
\textup{(}Proposition~\textup{\ref{prop:e1-nonsplitting-obstruction}}\textup{)}.
\end{proof}

\begin{table}[ht]
\centering
\small
\caption{Five-theorem scope for
$\operatorname{Sym}^N(X)$.}\label{tab:symn-five-theorems}
\begin{tabular}{p{2.5cm}p{6.6cm}p{4.2cm}}
\toprule
\textbf{Theorem} & \textbf{Statement for $\operatorname{Sym}^N(X)$}
 & \textbf{Scope} \\
\midrule
A (adjunction) &
 completed bar--cobar adjunction for the fixed-point algebra;
 twisted completion separate
 & Conj.~\ref{conj:symn-koszul-dual} \\
B (inversion) &
 $\Omega(\widehat{\barB}(X_N^{\mathrm{id}}))\to X_N^{\mathrm{id}}$
 & Reynolds descent hypothesis; Prop.~\ref{conj:symn-inversion} \\
C (complementarity) &
 finite-type identity sector:
 $\kappa+\kappa^!=N(\kappa(X)+\kappa(X^!))$
 & Rem.~\ref{rem:symn-complementarity} \\
D (modular char.) &
 $\kappa^{\mathrm{id}}_1(X_N^{\mathrm{id}})=N\kappa(X)$
 & Prop.~\ref{prop:symn-kappa} \\
H (chiral Hochschild) &
 $\operatorname{ChirHoch}^n(X_N^{\mathrm{id}})=0$ for $n>2$
 & completed PBW/perfect lane; Prop.~\ref{conj:symn-hochschild} \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\small
\caption{Five noninterchangeable registers for the fixed-point and
completed orbifold objects.}\label{tab:symn-register-firewall}
\begin{tabular}{p{3.0cm}p{5.0cm}p{5.0cm}}
\toprule
\textbf{Register} & \textbf{Fixed-point object}
 & \textbf{Completed orbifold object} \\
\midrule
Chiral homology &
 $\int_C^{\mathrm{ch}} X_N^{\mathrm{id}}$ on the chosen curve~$C$ &
 requires a specified $G$-crossed chiral algebra \\
Chiral Hochschild &
 $\ChirHoch^\bullet(X_N^{\mathrm{id}})$ &
 Hochschild complex of the completed OPE algebra \\
Verdier duality &
 $(X_N^{\mathrm{id}})^!$ after bar cohomology and Verdier duality &
 computed only after twisted OPE data are installed \\
Bar--cobar inversion &
 $\Omega\widehat{\barB}(X_N^{\mathrm{id}})\to X_N^{\mathrm{id}}$ &
 a separate completed counit \\
Physical bulk &
 not $\barB(X_N^{\mathrm{id}})$ and not $(X_N^{\mathrm{id}})^!$ &
 model-dependent open--closed comparison \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\small
\caption{Shadow archetype data for the fixed-point
sector.}\label{tab:symn-shadow-archetype}
\begin{tabular}{ll}
\toprule
\textbf{Invariant} & \textbf{Value} \\
\midrule
Diagonal class & Same as seed $X$ \\
Shadow depth $r_{\max}$ &
 at least $r_{\max}(X)$ in the diagonal fixed-point channel \\
$\kappa^{\mathrm{id}}_1(X_N^{\mathrm{id}})$ &
 $N \cdot \kappa(X)$ \\
Identity-sector $F_1$ & $N \cdot \kappa(X) / 24$ \\
Koszul dual &
 Verdier dual after fixed-point Reynolds descent; not
 $\Omega\barB$ \\
Complementarity (identity sector) &
 $N \cdot (\kappa(X) + \kappa(X^!))$ \\
\bottomrule
\end{tabular}
\end{table}

\begin{proposition}[Identity-sector modular characteristic;
\ClaimStatusProvedHere]\label{prop:symn-kappa}
\index{symmetric orbifold!modular characteristic}
Let $N\geq1$, and let $X$ be a modular Koszul chiral algebra with
finite-dimensional graded pieces, completed along the weight
filtration, and with genus-$1$ scalar obstruction
$\mathrm{obs}_1(X)=\kappa(X)\lambda_1$ defined as a finite scalar
class. For the fixed-point chiral algebra
$X_N^{\mathrm{id}}=(X^{\otimes N})^{S_N}$,
\[
 \kappa^{\mathrm{id}}_1(X_N^{\mathrm{id}})
 \;=\; N \cdot \kappa(X).
\]
This is the identity-sector scalar obstruction. It is not a
statement about the full twisted orbifold Hilbert space, a
higher-genus free energy, or the ordered bar complex of a
$G$-crossed orbifold completion. Singular parameter values at which
the seed scalar lane is not finite are outside the statement; no
genericity is otherwise used.
\end{proposition}

\begin{proof}
The tensor product $X^{\otimes N}$ has diagonal stress tensor and
diagonal obstruction cocycle equal to the sum of the $N$ copywise
cocycles. Additivity of the scalar obstruction for independent
tensor factors gives
\[
 \mathrm{obs}_1(X^{\otimes N})
 = \sum_{i=1}^N \mathrm{obs}_1(X^{(i)})
 = N\,\kappa(X)\lambda_1 .
\]
The Reynolds idempotent
$\frac1{N!}\sum_{\sigma\in S_N}\sigma$ fixes the diagonal cocycle.
Thus the invariant chiral algebra $X_N^{\mathrm{id}}$ carries the
same diagonal scalar obstruction. Exactness of finite-group
invariants over characteristic zero gives the fixed-point passage in
each finite weight window, and completion is taken after
the finite-window calculation. No twisted-sector state is used in
this computation.
\end{proof}

\begin{remark}[K3 elliptic genus and the identity scalar]
\label{rem:symn-k3-elliptic-identity}
For the CY$_2$ sigma-model scalar lane used here,
$\kappa(K3)=2$. This is the categorical/CY scalar, not the
Virasoro curvature $c/2=3$ of the $c=6$ stress tensor.
Proposition~\ref{prop:symn-kappa} gives
$\kappa^{\mathrm{id}}_1((K3^{\otimes N})^{S_N})=2N$.
The DMVV formula \cite{DMVV97} instead concerns the elliptic genus:
if
\[
 \operatorname{Ell}_{K3}(\tau,z)
 =\sum_{n,\ell}c_{K3}(n,\ell)q^n y^\ell,
\]
then
\[
 \sum_{N\geq0}p^N
 \operatorname{Ell}_{\operatorname{Sym}^N(K3)}(\tau,z)
 =
 \prod_{\substack{m\geq1,\; n\geq0\\ \ell}}
 (1-p^m q^n y^\ell)^{-c_{K3}(mn,\ell)} .
\]
At $z=0$ this specializes to
$\sum_N p^N\chi(\operatorname{Hilb}^N(K3))
=\prod_{m\geq1}(1-p^m)^{-24}$.
This partition-function identity includes all commuting-pair
orbifold sectors. It is compatible with the identity-sector scalar,
but it is not a proof of ordered-bar linearity.
\end{remark}

% ======================================================================
% Section: Twist sectors and vacuum energy
% ======================================================================

\section{Twist sectors and vacuum energy}\label{sec:symn-twist-sectors}

The full orbifold Hilbert space $\mathcal H_N^{\mathrm{orb}}$
decomposes over conjugacy classes of~$S_N$. Each conjugacy class is
parametrized by
a partition $\lambda = (1^{m_1}\, 2^{m_2} \cdots k^{m_k})$ of~$N$,
and the twist field associated to a permutation of cycle type~$\lambda$
has conformal weight \cite{LuninMathur2001}
\begin{equation}\label{eq:symn-twist-weight}
 h_{\mathrm{twist}}(\lambda)
 \;=\; \frac{c(X)}{24}\, \sum_{j=1}^{k} m_j\Bigl(j - \frac{1}{j}\Bigr).
\end{equation}
The identity conjugacy class ($\lambda = (1^N)$) is the only
cycle type with twist energy zero; after the centralizer projection
it gives the fixed-point sector $X_N^{\mathrm{id}}$. For a single
transposition ($\lambda = (2, 1^{N-2})$):
$h_{\mathrm{twist}} = c(X)/16$, the lightest twist field when
$c(X)>0$.

\begin{proposition}[Twist weights and the identity vacuum;
\ClaimStatusProvedHere]\label{prop:symn-twist-vanishing}
\index{symmetric orbifold!twist sector weights}
Assume the seed conformal field theory is of CFT type, has
finite-dimensional conformal-weight spaces, and has $c(X)>0$. For
every nontrivial cycle type $\lambda\neq (1^N)$, the twist ground
state has $h_{\mathrm{twist}}(\lambda)>0$. Consequently no
nontrivial twist ground state lies in the identity-vacuum conformal
weight.
The identity-sector scalar in Proposition~\ref{prop:symn-kappa} is
therefore unaffected by adjoining the twisted Hilbert spaces.

The proposition does not assert that twisted sectors vanish from the
genus-$1$ partition function. They are precisely the additional
terms organized by the DMVV product. No positivity conclusion is
asserted at $c(X)\leq0$ or in singular non-CFT-type quotients.
\end{proposition}

\begin{proof}
For $\lambda=(1^{m_1}2^{m_2}\cdots k^{m_k})$,
\[
 h_{\mathrm{twist}}(\lambda)
 = \frac{c(X)}{24}\sum_{j=1}^k m_j\Bigl(j-\frac1j\Bigr).
\]
Each summand is nonnegative and it is positive for every cycle of
length $j>1$. A nontrivial conjugacy class contains such a cycle, so
$h_{\mathrm{twist}}(\lambda)>0$ when $c(X)>0$. The identity
conjugacy class is therefore the only sector with zero twist
energy; if the seed theory is of CFT type, this sector contains the
unique vacuum vector. At $c(X)\leq0$ this positivity argument
disappears; no conclusion about the twisted contribution follows
from the weight formula alone.
\end{proof}

\begin{remark}[Twisted sectors and bar degree]
\label{rem:symn-twist-higher-degree}
\index{symmetric orbifold!twisted sector shadows}
There is no universal ``first quartic correction'' theorem. In the
fixed-point chiral algebra $X_N^{\mathrm{id}}$, twist fields are
modules rather than bar generators. In a $G$-crossed completion that
adjoins twist fields, the binary OPE
\[
 \sigma_g(z)\sigma_h(w)\sim
 (z-w)^{-\alpha(g,h)}\,\sigma_{gh}(w)+\cdots
\]
already enters the bar differential. For $N=2$ the covering-space
calculation of Lunin--Mathur \cite{LuninMathur2001} gives the leading
branch exponent $\alpha=c(X)/8$ in the $\sigma_2$--$\sigma_2$
channel. The degree at which twisted data first changes a shadow
coefficient is therefore part of the chosen orbifold completion, not
a consequence of DMVV.
\end{remark}

\begin{conjecture}[Orbifold Koszul duality;
\ClaimStatusConjectured]\label{conj:symn-koszul-dual}
\index{symmetric orbifold!Koszul dual}
On the finite-type completed PBW lane, the Koszul dual of the
fixed-point algebra $X_N^{\mathrm{id}}$ is obtained from the
$S_N$-equivariant Koszul dual of $X^{\otimes N}$ only after the
Reynolds bar comparison is a filtered quasi-isomorphism. For a
$G$-crossed orbifold completion, additional summands are controlled
by the twist-field OPE algebra, not by $\operatorname{Sym}^N(X^!)$
alone. Singular quotient regimes require their own Reynolds and
twist-OPE calculations.
Here $X^!$ denotes the Verdier-side Koszul dual algebra extracted
from bar cohomology. It is not the cobar inverse
$\Omega\barB(X)$.
\end{conjecture}

\begin{proposition}[Bar-cobar inversion under Reynolds descent;
\ClaimStatusConditional]\label{conj:symn-inversion}
The bar-cobar counit
$\Omega(\widehat{\barB}(X_N^{\mathrm{id}})) \to X_N^{\mathrm{id}}$
is a quasi-isomorphism on the finite-type completed lane if $X$ is
chirally Koszul and the natural Reynolds comparison
\[
 \widehat{\barB}(X_N^{\mathrm{id}})
 \longrightarrow
 \widehat{\barB}(X^{\otimes N})^{S_N}
\]
is a filtered quasi-isomorphism. No assertion is made at singular
levels where the completed bar complex loses finite-type
perfectness.
\end{proposition}

\begin{proof}
Koszulness of $X$ gives completed bar-cobar inversion for each
tensor factor, and Proposition~\ref{prop:independent-sum-factorization}
gives the tensor-product statement for $X^{\otimes N}$. Over
characteristic zero the finite-group invariants functor is exact in
each finite weight window, so inversion descends along the displayed
comparison once that comparison is a filtered quasi-isomorphism.
Completion is taken after the weightwise descent. The comparison is
the only extra hypothesis; it is exactly the assertion that taking
the fixed-point chiral algebra introduces no higher bar torsion.
\end{proof}

\begin{remark}[Identity-sector complementarity]
\label{rem:symn-complementarity}
\index{symmetric orbifold!complementarity}
In the identity sector, complementarity
(Theorem~\ref{thm:quantum-complementarity}) for the tensor product
$X^{\otimes N}$ gives
$\kappa(X^{\otimes N}) + \kappa((X^!)^{\otimes N}) =
N(\kappa(X) + \kappa(X^!))$. The fixed-point comparison requires the
same Reynolds descent as Proposition~\ref{conj:symn-inversion}. A
twisted orbifold completion has its own chiral derived centre and
its own chiral Hochschild complex; the physical $3$d bulk, if
present, is related by an open--closed comparison rather than by
identifying it with $\barB(X_N^{\mathrm{id}})$ or
$(X_N^{\mathrm{id}})^!$. Theorem~C for that completed object is a
separate theorem.
\end{remark}

\begin{proposition}[Theorem H for the fixed-point sector;
\ClaimStatusConditional]\label{conj:symn-hochschild}
If $X_N^{\mathrm{id}}$ is chirally Koszul on the completed finite-type
PBW lane and the compact-generation/perfectness hypotheses of
Theorem~\ref{thm:hochschild-polynomial-growth} hold for the
fixed-point chiral algebra, then
\[
 \operatorname{ChirHoch}^n(X_N^{\mathrm{id}})=0
 \qquad (n>2).
\]
This is an ambient-curve statement. It does not compute the
categorical Hochschild cohomology of the full twisted orbifold
module category, and it does not apply automatically at singular
quotient parameters where the hypotheses of
Theorem~\ref{thm:hochschild-polynomial-growth} fail.
\end{proposition}

\begin{proof}
Theorem~\ref{thm:hochschild-polynomial-growth} is applied to the
single chiral algebra $X_N^{\mathrm{id}}$ on a smooth projective
curve. Its amplitude bound is the curve bound $[0,2]$. Twisted
sectors are modules for $X_N^{\mathrm{id}}$ unless a separate
$G$-crossed algebra has been constructed, so they are not inputs to
this chiral Hochschild complex. The completed finite-type and
perfectness hypotheses are precisely those required to make the
Hochschild dimensions finite and the curve-level duality shift
available.
\end{proof}


% ======================================================================
% Section: Diagonal shadow depth
% ======================================================================

\section{Diagonal shadow depth}\label{sec:symn-shadow-depth}

\begin{proposition}[Diagonal shadow depth of the fixed-point sector;
\ClaimStatusProvedHere]\label{prop:symn-shadow-depth}
\index{symmetric orbifold!shadow depth}
Let $N\geq1$, and let $X$ be a modular Koszul algebra. For the
fixed-point chiral algebra
$X_N^{\mathrm{id}}=(X^{\otimes N})^{S_N}$, the diagonal fixed-point
channels in the completed finite-type bar surface satisfy
\begin{equation}\label{eq:symn-shadow-depth-bound}
 r_{\max}(X_N^{\mathrm{id}})
 \;\geq\; r_{\max}(X).
\end{equation}
If $X$ is class~M, the diagonal Virasoro field
$T_\Delta=\sum_iT^{(i)}$ gives
$r_{\max}(X_N^{\mathrm{id}})=\infty$ on the generic class-M lane.
At singular quotient values the statement applies only after the
seed channel witnessing $r_{\max}(X)$ survives in the quotient.
\end{proposition}

\begin{proof}
Let $u(z)v(w)$ be a seed OPE channel witnessing shadow depth~$r$.
Set $u_\Delta=\sum_i u^{(i)}$ and
$v_\Delta=\sum_i v^{(i)}$. Mixed-copy OPEs are regular, hence the
singular part of $u_\Delta(z)v_\Delta(w)$ is the sum of the $N$
copywise singular parts. The highest nonzero pole or shadow
coefficient is therefore multiplied by $N$, not cancelled. Since
the diagonal fields are $S_N$-invariant, the same channel lies in
$X_N^{\mathrm{id}}$. For class~M the seed Virasoro channel has
unbounded shadow depth, and the diagonal Virasoro channel has the
same unbounded depth.
\end{proof}

\begin{remark}[Shadow class of specific orbifolds]
\label{rem:symn-shadow-class-examples}
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lccl}
\toprule
Seed $X$ & Class of $X$ & $r_{\max}(X)$ &
 Fixed-point conclusion \\
\midrule
Heisenberg $\mathcal{H}_\kappa$ & G & $2$ &
 diagonal depth $\geq2$; exact class open \\
$\widehat{\mathfrak{sl}}_2$ at level $k$ & L & $3$ &
 diagonal depth $\geq3$; exact class open \\
$\beta\gamma$ & C & $4$ &
 diagonal depth $\geq4$; exact class open \\
$\mathrm{Vir}_c$ & M & $\infty$ & M \\
$K3$ $\mathcal N=4$ matter lane & M & $\infty$ & M \\
\bottomrule
\end{tabular}
\end{center}
For class~M seeds, a non-formal diagonal channel forces infinite
depth in $X_N^{\mathrm{id}}$. For class~G, L, or C seeds, the table
records only the inherited diagonal lower bound; invariant composite
fields in $X_N^{\mathrm{id}}$ may raise the fixed-point depth beyond
the seed value. A $G$-crossed completion may raise it again through
twist-field OPEs. These are two different questions.
\end{remark}


% ======================================================================
% Section: Fixed-point Koszulness
% ======================================================================

\section{Fixed-point Koszulness}
\label{sec:symn-koszulness}

\begin{proposition}[Tensor-product Koszulness and fixed-point descent;
\ClaimStatusConditional]\label{prop:symn-koszulness}
\index{symmetric orbifold!Koszulness}
Let $N\geq1$. If the seed algebra~$X$ is freely strongly generated
in finite weight windows, complete for the weight filtration, and
hence chirally Koszul on the PBW/generic lane
(Proposition~\textup{\ref{prop:pbw-universality}}), then the
tensor product $X^{\otimes N}$ is chirally Koszul. The fixed-point
algebra $X_N^{\mathrm{id}}$ is chirally Koszul if the Reynolds
comparison
\[
 \widehat{\barB}(X_N^{\mathrm{id}})
 \longrightarrow
 \widehat{\barB}(X^{\otimes N})^{S_N}
\]
is a filtered quasi-isomorphism. Singular simple quotients where
PBW freeness or finite-type perfectness fails are outside this
conditional statement unless the displayed comparison is verified
directly there.
\end{proposition}

\begin{proof}
The tensor product of freely strongly generated algebras is freely
strongly generated: if $\{a_i\}$ are free strong generators of~$X$,
then $\{a_i^{(r)}\}_{r=1}^N$ (the $i$-th generator in the $r$-th
copy) are free strong generators of $X^{\otimes N}$. PBW
universality (Proposition~\ref{prop:pbw-universality}) applies to
$X^{\otimes N}$, giving bar concentration. If the displayed completed
Reynolds comparison is a filtered quasi-isomorphism, then
\[
 H^\bullet\widehat{\barB}(X_N^{\mathrm{id}})
 \cong H^\bullet(\widehat{\barB}(X^{\otimes N})^{S_N}).
\]
Over characteristic zero, $S_N$-invariants are exact, so the right
side is $H^\bullet\widehat{\barB}(X^{\otimes N})^{S_N}$ and remains
concentrated in the same bar degree, weight by weight.
\end{proof}

\begin{remark}[The two Koszul obstructions]
\label{rem:symn-full-koszulness}
Two independent obstructions remain after the tensor-product
calculation. First, fixed-point vertex algebras can have
invariant-theoretic relations even when the original tensor product
is freely strongly generated; this is measured by the Reynolds
comparison. Second, a $G$-crossed completion has twist fields and
binary twist OPEs, so its bar differential is not controlled by PBW
universality for $X^{\otimes N}$.
\end{remark}


% ======================================================================
% Section: The DMVV formula and second quantization
% ======================================================================

\section{The DMVV formula and second quantization}\label{sec:symn-dmvv}

The genus-$1$ elliptic genus of the full permutation-orbifold
conformal field theory has a closed expression in terms of the seed
elliptic genus. The DMVV product \cite{DMVV97} computes the
generating series over all~$N$ simultaneously:
for a seed theory~$X$ with elliptic genus
$Z_X(\tau, z) = \sum_{n,\ell} c_X(n,\ell)\, q^n y^\ell$,
\begin{equation}\label{eq:symn-dmvv}
 \mathcal Z_X(p,\tau,z)
 :=
 \sum_{N \geq 0} p^N\, Z(\operatorname{Sym}^N(X);\, \tau, z)
 \;=\; \prod_{\substack{n \geq 0,\; m \geq 1 \\ \ell}}
 \bigl(1 - q^n\, y^\ell\, p^m\bigr)^{-c_X(mn,\, \ell)}.
\end{equation}
The formula is a second-quantized lift: the genus-$1$ data of
the seed~$X$ (the Fourier coefficients $c_X(n, \ell)$) generate
the full orbifold partition function at all~$N$ through a
Borcherds-type infinite product. Its input and output are
elliptic genera, not ordered bar complexes.

\begin{proposition}[Cycle-index and plethystic normalization;
\ClaimStatusProvedHere]\label{prop:symn-cycle-index-plethystic}
\index{DMVV formula!cycle-index normalization}
\index{plethystic exponential!symmetric orbifold}
Assume the seed elliptic genus has finite-dimensional graded
coefficients. With the normalized Hecke operator $V_j$ of
\eqref{eq:symn-hecke-operator},
\[
 \mathcal Z_X(p,\tau,z)
 =
 \exp\Bigl(\sum_{j\geq1}p^jV_jZ_X(\tau,z)\Bigr).
\]
Consequently, for a partition
$\lambda=(1^{m_1}2^{m_2}\cdots)\vdash N$,
\begin{equation}\label{eq:symn-cycle-index}
 [p^N]\,\mathcal Z_X
 =
 \sum_{\lambda\vdash N}
 \prod_{j\geq1}
 \frac{\bigl(V_jZ_X\bigr)^{m_j}}{m_j!}.
\end{equation}
The factors $j^{-m_j}$ from the cyclic centralizers are already
inside $V_j$; the factors $(m_j!)^{-1}$ are the symmetric products
of equal-length cycles. This is the cycle-index/plethystic
normalization of DMVV, not an ordered-bar Hilbert series.
\end{proposition}

\begin{proof}
Dijkgraaf--Moore--Verlinde--Verlinde \cite{DMVV97} decompose the
orbifold Hilbert space as
$\bigoplus_{[\sigma]}\mathcal H_\sigma^{C(\sigma)}$ and write a
conjugacy class as
$\lambda=(1^{m_1}2^{m_2}\cdots)$, with centralizer
\[
 C(\sigma)
 =
 \prod_{j\geq1}\bigl(S_{m_j}\ltimes \mathbb Z_j^{m_j}\bigr).
\]
The cyclic factors produce the $1/j$ normalization in the connected
length-$j$ Hecke term $V_jZ_X$, and the symmetric factors produce
the $1/m_j!$ coefficient in the exponential. Expanding the
plethystic exponential gives~\eqref{eq:symn-cycle-index}. The
derivation is a trace calculation over twisted Hilbert spaces; no
ordered bar generator appears.
\end{proof}

\begin{remark}[DMVV as an elliptic-genus lift]
\label{rem:symn-dmvv-shadow}
\index{DMVV formula!shadow interpretation}
The logarithm of the DMVV product is the Hecke expansion of the
seed elliptic genus. It records the full genus-$1$ orbifold
spectrum, including commuting-pair twisted sectors. A shadow
coefficient of the ordered bar complex can be compared with this
series only after specifying a projection to the identity-sector
vacuum anomaly. There is no implication
$F_g(\operatorname{Sym}^N(X))=N F_g(X)$ for $g\geq2$ from DMVV.
\end{remark}

For $X = K3$, the product is related to the unscaled Igusa cusp
form~$\Phi_{10}^{\mathrm{un}}$ by the Fourier--Jacobi normalization
\[
 \mathcal Z_{K3}(p,\tau,z)
 =
 \frac{p\,\phi_{10,1}(\tau,z)}
      {\Phi_{10}^{\mathrm{un}}(\tau,z,\sigma)},
 \qquad p=e^{2\pi i\sigma}.
\]
Thus $1/\Phi_{10}^{\mathrm{un}}$ itself carries the Weyl-vector
prefactor $p^{-1}/\phi_{10,1}$ at the cusp; it is not the DMVV
series without this normalization. At the Euler-characteristic
specialization one obtains
$\sum_N p^N \chi(\operatorname{Hilb}^N(K3))
= \prod_{n \geq 1}(1 - p^n)^{-24}$.

\begin{proposition}[DMVV does not compute ordered-bar $\kappa$;
\ClaimStatusProvedHere]\label{prop:symn-dmvv-kappa}
\index{DMVV formula!kappa separation}
The coefficient of $p^N$ in the DMVV series~\eqref{eq:symn-dmvv}
is the full genus-$1$ orbifold elliptic genus, with cycle-index
normalization~\eqref{eq:symn-cycle-index}. For $N>1$ it is not the
identity-sector ordered-bar scalar $N\kappa(X)/24$. Any extraction
of Proposition~\ref{prop:symn-kappa} from DMVV requires an
additional projection to the diagonal vacuum-anomaly summand. This
is a finite-coefficient genus-$1$ elliptic-genus statement, not a
claim about higher genus, completed bar cohomology, or singular
parameter loci.
\end{proposition}

\begin{proof}
Taking the logarithm of~\eqref{eq:symn-dmvv} gives the explicit
covering expansion
\[
 \log\mathcal Z_X(p,\tau,z)
 =
 \sum_{\substack{r\geq1,\; m\geq1\\ n\geq0,\;\ell}}
 \frac{c_X(mn,\ell)}{r}\,
 p^{rm}q^{rn}y^{r\ell}.
\]
Thus the connected $p^N$ coefficient is the divisor sum over
$rm=N$, equivalently the normalized Hecke transform of the seed
elliptic genus. The coefficient of the original exponential also
contains products indexed by partitions of~$N$. These terms include
non-identity covering data and twisted sectors. They are part of the
elliptic genus and have no canonical identification with the ordered
bar differential of $X_N^{\mathrm{id}}$.
\end{proof}


% ======================================================================
% Section: Large-N limit and holography
% ======================================================================

\section{Large-$N$ limit and holography}\label{sec:symn-large-N}

The identity-sector scalar
$\kappa^{\mathrm{id}}_1(X_N^{\mathrm{id}})=N\kappa(X)$ grows
linearly with~$N$. The full symmetric-orbifold free energy is a
different object: it is extracted from the DMVV product and depends
on the polar spectrum and the choice of large-$N$ regime.

In a Cardy or holographic scaling limit one may write an expansion
\begin{equation}\label{eq:symn-large-N-expansion}
 \log Z(\operatorname{Sym}^N)
 \;=\; N f_0 + f_1 + N^{-1} f_2 + \cdots
\end{equation}
after fixing the ensemble and the normalization of $Z$. The
identity-sector scalar gives only the genus-$1$ diagonal anomaly:
\begin{equation}\label{eq:symn-genus-scaling}
 F^{\mathrm{id}}_1(\operatorname{Sym}^N(X))
 \;=\; \frac{N\kappa(X)}{24}.
\end{equation}
It does not determine the higher-genus coefficients $f_g$ of the
full orbifold partition function.

\begin{remark}[The $1/N$ expansion is not a bar theorem]
\label{rem:symn-genus-vs-1-over-N}
The string-theoretic rule $g_s\sim N^{-1/2}$ predicts genus-$g$
weights $N^{1-g}$ for connected closed-string amplitudes. The
ordered-bar scalar gives the boundary identity-sector anomaly
$N\kappa(X)$, not the whole closed-string genus expansion. A theorem
identifying higher shadow coefficients with bulk loop amplitudes
requires the Costello--Paquette bulk-boundary comparison and a
specified completion; it is not a consequence of DMVV or of
Proposition~\ref{prop:symn-kappa}.
\end{remark}

For $X = T^4$ or $K3$, Costello--Paquette
\cite{CP2020} identify, in their twisted $\mathrm{AdS}_3$ setting,
the large-$N$ boundary chiral algebra with the free symmetric
orbifold and the Kodaira--Spencer theory with the physical
holographic bulk. This is a bulk-boundary comparison theorem in
that physical model. It is not, by itself, an identification of
the chiral derived centre $Z^{\mathrm{der}}_{\mathrm{ch}}(X_N)$,
the Verdier-side Koszul dual $X_N^!$, or the ordered bar coalgebra
$\barB^{\mathrm{ord}}(X_N)$ with the physical bulk. On the K3
identity lane, $\kappa^{\mathrm{id}}_1=2N$ while the
Brown--Henneaux central charge is $c=6N$; the anomaly ratio is
$\varrho=\kappa/c=1/3$, not the Virasoro ratio~$1/2$.


% ======================================================================
% Section: BTZ entropy and the shadow tower
% ======================================================================

\section{BTZ entropy and the shadow tower}\label{sec:symn-btz}

In a unitary Cardy regime with a specified bulk normalization, the
BTZ black hole entropy is
\begin{equation}\label{eq:symn-btz}
 S_{\mathrm{BH}}
 \;=\; 2\pi\sqrt{\frac{c \cdot n}{6}}
 \;=\; 2\pi\sqrt{\frac{\kappa \cdot n}{6\varrho}}
\end{equation}
where $n=L_0-c/24$ and $\varrho=\kappa/c$ on the chosen anomaly
lane. Cardy asymptotics determine the central charge. They determine
$\kappa$ only after the lane-specific ratio~$\varrho$ is fixed. For
the K3 symmetric-orbifold lane, $c=6N$, $\kappa=2N$, and
$\varrho=1/3$, giving
$S_{\mathrm{BH}}=2\pi\sqrt{Nn}$.

\begin{remark}[Logarithmic corrections and shadow data]
\label{rem:symn-btz-log-corrections}
\index{BTZ black hole!logarithmic corrections}
For a pure BTZ saddle with no extra light fields, the first
logarithmic correction has the standard form
\[
 S_{\mathrm{BH}}
 \;=\; 2\pi\sqrt{\frac{c n}{6}}
 \;-\; \frac{3}{2}\log\Bigl(\frac{c n}{6}\Bigr)
 \;+\; O(1),
\]
with the coefficient depending on the one-loop field content. Higher
ordered-bar shadows are boundary invariants which may enter a
specified bulk-boundary comparison, but they do not universally
determine the $O(1)$ Rademacher or one-loop terms of the full
orbifold spectrum.
\end{remark}


% ======================================================================
% Section: The N=2 fixed-point and transposition sectors
% ======================================================================

\section{The \texorpdfstring{$N = 2$}{N = 2} orbifold:
fixed-point and transposition sectors}\label{sec:symn-n2-explicit}

The simplest nontrivial symmetric orbifold is
$X_2^{\mathrm{id}}=(X\otimes X)^{\mathbb Z_2}$. The full
permutation-orbifold CFT also has the transposition sector $(12)$,
which carries one family of twist fields.

\begin{computation}[$\operatorname{Sym}^2(X)$ invariants]
\label{comp:sym2-explicit}
\index{symmetric orbifold!N=2 explicit}
Let $X$ be a chirally Koszul seed on the completed finite-type lane,
with central charge $c(X)$ and modular characteristic $\kappa(X)$.
The fixed-point identity sector has:
\begin{align}
 c(X_2^{\mathrm{id}})
 &= 2c(X), \label{eq:sym2-c} \\
 \kappa^{\mathrm{id}}_1(X_2^{\mathrm{id}})
 &= 2 \kappa(X), \label{eq:sym2-kappa} \\
 F^{\mathrm{id}}_1(\operatorname{Sym}^2(X))
 &= \kappa(X) / 12, \label{eq:sym2-f1}
\end{align}
by Proposition~\ref{prop:symn-kappa}. The transposition sector
contributes to the full orbifold genus-$1$ partition function, but
it does not enter the ordered bar complex of $X_2^{\mathrm{id}}$.
\end{computation}

\begin{remark}[The twist field at $N = 2$]
\label{rem:sym2-twist-field}
\index{twist field!N=2}
The transposition $(12) \in S_2$ introduces a twist field
$\sigma_2$ of conformal weight
\begin{equation}\label{eq:sym2-twist-weight}
 h(\sigma_2) \;=\; \frac{c(X)}{16}.
\end{equation}
For the K3 sigma-model central charge $c(X)=6$, this gives
$h(\sigma_2)=3/8$.
The twist-field OPE is computed by the covering-space method:
the two-sheeted branched cover $\pi \colon \Sigma \to
\mathbb{P}^1$ ramified at the twist-field insertion points
maps the orbifold correlator to a correlator on the
covering surface~$\Sigma$. The leading
$\sigma_2$--$\sigma_2$ branch factor is
$(z-w)^{-c(X)/8}$, coming from the Casimir energy of the
two-sheeted cover. This is a branch exponent in the twisted module
category, not an ordinary meromorphic pole order in the fixed-point
chiral algebra.
\end{remark}

\begin{remark}[Covering space and the bar complex]
\label{rem:sym2-covering-bar}
\index{symmetric orbifold!covering space}
The covering-space technology has a bar-complex interpretation only
after the object has been chosen. For the fixed-point algebra,
\[
 \barB^{\mathrm{ord}}(X_2^{\mathrm{id}})
 = T^c\bigl(s^{-1}\overline{(X\otimes X)^{\mathbb Z_2}}\bigr),
\]
and the generators are invariant fields. There are no desuspended
twist fields in this complex.

For a $G$-crossed completion that adjoins $\sigma_2$, the bar
complex has three families of tensors:
\begin{enumerate}
\item invariant--invariant tensors inherited from
 $(X\otimes X)^{\mathbb Z_2}$;
\item The \emph{twist-twist} sector:
 tensor products of desuspended twist fields
 $s^{-1}\sigma_2 \otimes s^{-1}\sigma_2$, whose bar
 differential involves the $\sigma_2$-$\sigma_2$ OPE.
\item The \emph{mixed} sector: tensor products involving both
 untwisted and twist-field generators, with the bar
 differential involving mixed OPE data.
\end{enumerate}
The invariant-sector Koszul question is the Reynolds comparison of
Proposition~\ref{prop:symn-koszulness}. The completed-orbifold
Koszul question is the additional twist-OPE calculation.
\end{remark}


% ======================================================================
% Section: Hecke operators and the Fock space structure
% ======================================================================

\section{Hecke operators and the Fock space structure}
\label{sec:symn-hecke}

The DMVV formula~\eqref{eq:symn-dmvv} has a Hecke-operator form.
The generating series
$\sum_{N \geq 0} p^N Z(\operatorname{Sym}^N(X))$ can be
reorganized using the normalized Hecke operator $V_m$ acting on
the seed elliptic genus:
\begin{equation}\label{eq:symn-hecke}
 \sum_{N \geq 0} p^N\, Z(\operatorname{Sym}^N(X);\, \tau, z)
 \;=\; \exp\Bigl(\sum_{m \geq 1} p^m\,
 V_m\, Z_X(\tau, z)\Bigr),
\end{equation}
where
\begin{equation}\label{eq:symn-hecke-operator}
 V_m Z_X(\tau, z)
 =
 \frac{1}{m}\sum_{ad = m,\, 0 \leq b < d}
 Z_X\bigl(\frac{a\tau + b}{d},\, az\bigr).
\end{equation}
If $\mathsf H_m$ denotes the raw covering sum, then
$V_m=\mathsf H_m/m$. This normalization is the one whose Fourier
expansion is the logarithm of the DMVV product.

\begin{remark}[Fock space interpretation]
\label{rem:symn-fock}
\index{symmetric orbifold!Fock space}
The exponential in~\eqref{eq:symn-hecke} identifies the
symmetric orbifold partition function with the partition
function of a \emph{bosonic Fock space} built from the
Hecke-transformed seed elliptic genus. The ``single-particle''
object is the graded vector space counted by the seed elliptic
genus, not the ordered bar complex of the seed VOA. The Hecke
operators organize covering data of the torus. They do not act as
creation operators on the chiral bar complex and do not imply
$S_r(\operatorname{Sym}^N(X))=N S_r(X)$.
\end{remark}

\begin{remark}[K3 seed and the genus-$2$ Igusa character]
\label{rem:symn-k3-igusa-character}
For the K3 seed one has the classical DMVV identity
\[
 \sum_{N\geq 0} p^N\,Z\bigl(\operatorname{Sym}^N(K3);\tau,z\bigr)
 \;=\;
 \frac{p\,\phi_{10,1}(\tau,z)}
      {\Phi_{10}^{\mathrm{un}}(\tau,z,\sigma)}.
\]
Two boundary regimes of the reciprocal Siegel form must be kept
distinct. The Fourier--Jacobi cusp $p\to 0$ gives
\[
 \frac{1}{\Phi_{10}^{\mathrm{un}}(\tau,z,\sigma)}
 \;=\;
 \frac{p^{-1}}{\phi_{10,1}(\tau,z)} + O(p^0),
 \qquad
 \phi_{10,1}(\tau,z)=\eta(\tau)^{18}\vartheta_1(\tau,z)^2.
\]
The separating divisor $z\to 0$ gives
\[
 \frac{1}{\Phi_{10}^{\mathrm{un}}(\tau,z,\sigma)}
 \;=\;
 -\frac{1}{4\pi^2 z^2\,\eta(\tau)^{24}\eta(\sigma)^{24}} + O(z^0).
\]
The DMVV series differs from this reciprocal by the factor
$p\,\phi_{10,1}$. Volume~III uses the reciprocal Siegel form as the
genus-$2$ character of the K3 chiral bialgebra
$\mathbf{H}_{\Delta_5}$; the first limit isolates the Jacobi
coefficient, while the second is the genuine separating degeneration.
\end{remark}

\begin{proposition}[Hecke operators and the identity scalar;
\ClaimStatusProvedHere]\label{prop:symn-hecke-kappa}
\index{Hecke operator!identity scalar}
Assume the seed elliptic genus has finite-dimensional graded
coefficients. The Hecke operator $V_1 = \mathrm{id}$ reproduces the
seed contribution, so the $p^1$ term of~\eqref{eq:symn-hecke}
is $Z_X(\tau, z)$ and the connected genus-$1$ amplitude at
$N = 1$ has identity scalar $F^{\mathrm{id}}_1(X)=\kappa(X)/24$.
For $N>1$, the Hecke coefficient is not the ordered-bar scalar
$N\kappa(X)/24$ without the identity-sector projection of
Proposition~\ref{prop:symn-kappa}.
\end{proposition}

\begin{proof}
The logarithm of~\eqref{eq:symn-hecke} gives the connected
elliptic-genus generating function:
$\sum_{N \geq 1} p^N F_1^{\mathrm{conn}}
(\operatorname{Sym}^N(X))
= \sum_{m \geq 1} p^m V_m Z_X$.
At order $p^N$: the connected genus-$1$ amplitude receives
contributions from the normalized $m = N$ Hecke operator acting on
the seed elliptic genus. Already for $N=2$,
\[
 [p^2]\,\mathcal Z_X
 =
 \frac{1}{2}Z_X^2 + V_2Z_X,
 \qquad
 V_2Z_X
 =
 \frac{1}{2}\Bigl(
 Z_X(2\tau,2z)
 +Z_X(\tau/2,z)
 +Z_X((\tau+1)/2,z)
 \Bigr).
\]
The constant terms are divisor-weighted Hecke sums, not the
diagonal copy sum in the ordered bar complex. The ordered-bar
scalar is recovered only by isolating the diagonal identity-sector
anomaly before taking the full orbifold trace.
\end{proof}


% ======================================================================
% Section: Fixed-point and completed-orbifold bar complexes
% ======================================================================

\section{Fixed-point and completed-orbifold bar complexes}
\label{sec:symn-bar-complex}

The ordered bar complex depends on which orbifold object is meant.
For the fixed-point chiral algebra it is the bar complex of
$X_N^{\mathrm{id}}=(X^{\otimes N})^{S_N}$; for a $G$-crossed
completion it is a larger complex with twisted generators.

\begin{computation}[Fixed-point bar complex]
\label{comp:symn-bar-decomposition}
\index{bar complex!symmetric orbifold}
The fixed-point ordered bar complex, completed weightwise when the
seed has infinitely many modes, is
\[
 \barB^{\mathrm{ord}}(X_N^{\mathrm{id}})
 =
 T^c\bigl(s^{-1}\overline{(X^{\otimes N})^{S_N}}\bigr).
\]
Its generators are invariant combinations of tensor-product fields,
for example diagonal generators
$a_\Delta=\sum_i a^{(i)}$ and higher invariant normally ordered
polynomials. The natural comparison map
\[
 \barB^{\mathrm{ord}}(X_N^{\mathrm{id}})
 \longrightarrow
 \barB^{\mathrm{ord}}(X^{\otimes N})^{S_N}
\]
is the Reynolds descent map of
Proposition~\ref{prop:symn-koszulness}. The further ordered-to-symmetric
projection in bar degree~$r$ is
$\operatorname{av}_{r,N}$ with kernel
$\mathcal K^{\mathrm{av}}_{r,N}(X)$
\textup{(}Definition~\ref{def:symn-averaging-kernel}\textup{)}.
Twist fields $\sigma_\lambda$ are absent from this complex. They
enter only after a $G$-crossed completion has been chosen.
\end{computation}

\begin{remark}[Collision residues of the fixed-point and twisted objects]
\label{rem:symn-r-matrix}
\index{symmetric orbifold!$R$-matrix}
The collision residue $r^{\mathrm{coll}}(z) =
\operatorname{Res}^{\mathrm{coll}}_{0,2}
(\Theta_{X_N^{\mathrm{id}}})$ has a diagonal fixed-point channel.
For the stress tensor,
\[
 T_\Delta(z)T_\Delta(w)
 \sim
 \frac{N\,c(X)/2}{(z-w)^4}
 + \frac{2T_\Delta(w)}{(z-w)^2}
 + \frac{\partial T_\Delta(w)}{z-w}.
\]
Thus the Virasoro collision residue has the same pole order as the
seed and scalar coefficient multiplied by~$N$.

Twist-twist channels are not meromorphic channels of
$X_N^{\mathrm{id}}$. In a completed orbifold category, the
$N=2$ field satisfies
\[
 T(z)\sigma_2(w)\sim
 \frac{(c/16)\sigma_2(w)}{(z-w)^2}
 +\frac{\partial\sigma_2(w)}{z-w},
 \qquad
 \sigma_2(z)\sigma_2(w)\sim
 (z-w)^{-c/8}(1+\cdots).
\]
The second formula is a branch expansion on the cover, not a pole of
integer order in the fixed-point VOA.
\end{remark}

\begin{remark}[Koszulness and the permutation orbifold
functor]\label{rem:symn-orbifold-functor}
\index{symmetric orbifold!orbifold functor}
The fixed-point construction defines the functor
$X\mapsto (X^{\otimes N})^{S_N}$ on vertex operator algebras. Its
Koszul question is whether the Reynolds comparison for bar complexes
is a quasi-isomorphism. A full permutation-orbifold CFT is not this
functor; it is the fixed-point algebra together with twisted modules,
and a $G$-crossed completion must specify their OPEs.

At the level of identity-sector modular characteristics,
$\kappa^{\mathrm{id}}_1(X_N^{\mathrm{id}})=N\kappa(X)$ by
Proposition~\ref{prop:symn-kappa}. Higher shadow coefficients and
twisted sectors are not functorial consequences of that scalar
identity.
\end{remark}

\begin{remark}[Comparison with the wreath product]
\label{rem:symn-wreath}
\index{symmetric orbifold!wreath product}
The permutation action is the vertex-algebra analogue of the wreath
product $\Gamma \wr S_N$ in finite group theory: the group $\Gamma$
(the automorphism group of~$X$) is wrapped by the symmetric group
$S_N$. When $\Gamma$ is trivial, the fixed-point algebra is
$(X^{\otimes N})^{S_N}$ and the full CFT still has permutation
twisted modules. When
$\Gamma = \mathbb{Z}_2$ (e.g., $X = \beta\gamma$ with its
$\mathbb{Z}_2$ symmetry), the wreath product
$\mathbb{Z}_2 \wr S_N$ acts on the tensor product, and the
fixed-point algebra is $(X^{\otimes N})^{\mathbb Z_2\wr S_N}$.
The completed CFT has both copywise $\mathbb Z_2$ twisted sectors
and permutation twisted sectors. Its Koszulness is a problem about
that completed OPE algebra, not a corollary of the fixed-point
scalar identity.
\end{remark}


% ======================================================================
% Section: Remaining open mathematical conditions
% ======================================================================

\section{Remaining open mathematical conditions}\label{sec:symn-open-problems}

\begin{enumerate}
\item \textbf{Reynolds descent.}
Decide when
$\widehat{\barB}((X^{\otimes N})^{S_N})
\to\widehat{\barB}(X^{\otimes N})^{S_N}$
is a filtered quasi-isomorphism. This is the fixed-point
Koszulness obstruction.

\item \textbf{Twisted-sector Koszul dual.}
Construct the $G$-crossed bar complex when twist fields are adjoined
and compute its Koszul dual from the twist-field OPE and
covering-space structure.

\item \textbf{Higher-genus orbifold amplitudes.}
The DMVV formula is a genus-$1$ elliptic-genus statement. Determine
which higher-genus amplitudes of the full orbifold CFT are fixed by
seed data and which require new twisted-sector sewing input.

\item \textbf{Exact shadow depth for non-M seeds.}
For class~G, L, or C seeds, determine whether invariant composite
fields in $X_N^{\mathrm{id}}$ increase the fixed-point shadow depth.
For completed orbifolds, repeat the calculation with twist-field
channels.
\end{enumerate}
