%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CHAPTER 66: TOROIDAL AND ELLIPTIC ALGEBRAS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Toroidal and elliptic algebras}
\label{chap:toroidal-elliptic}
% Regime IV : Programmatic (Convention~\ref{conv:regime-tags}).

Every chiral algebra in the preceding chapters depends on a single
deformation parameter: the level~$k$, the
central charge~$c$, or the spectral
parameter~$u$. This chapter enters the regime where one
parameter is not enough. The toroidal algebra
$U_{q,t}(\hat{\hat{\fg}})$ carries two independent parameters $(q,t)$,
the elliptic quantum group $E_{q,p}(\fg)$ replaces the rational
$R$-matrix by a doubly-periodic one, and the double affine Hecke
algebra (DAHA) intertwines spectral and modular directions. The modular parameter~$\tau$ and the
spectral parameter~$u$ are no longer independent:
the Fay trisecant identity and quasi-periodicity
of theta functions couple them.

The bar-cobar framework meets this two-parameter world in two ways.
Direction~(a) keeps the base a single algebraic curve of
genus~$1$: the propagator becomes elliptic, the Arnold relation
generalizes to the Fay trisecant identity
(Theorem~\ref{thm:fay}), and the bar differential acquires
Eisenstein-series corrections indexed by~$\tau$. The resulting
$\Eone$-chiral structures on $E_\tau$ sit inside the modular shadow
tower, with $\kappa(\cA)$ detecting the
$\tau$-dependence of the genus-$1$ obstruction. Direction~(b)
seeks genuine surface-factorization or double-affine objects on
$\bC^* \times \bC^*$, requiring a two-dimensional factorization
framework beyond the curve-chiral hierarchy of this
monograph. Only direction~(a) is developed here; direction~(b) is
a completion target.

The Fay identity replaces the Arnold relation at genus~$1$:
it is simultaneously an identity of theta functions and a geometric consequence of
the degeneration $E_\tau \to \mathbb{P}^1$ as $\tau \to i\infty$.

\begin{remark}[Two programme tracks]
\label{rem:toroidal-two-tracks}
Track~(a) keeps the base an algebraic curve and asks for an elliptic
$\Eone$-chiral realization on $E_\tau$. Track~(b) seeks a genuine
surface-factorization or double-affine object on
$\bC^* \times \bC^*$ or related two-parameter spaces. Only
track~(a) is described in this chapter with curve-chiral language;
track~(b) is a separate higher-dimensional completion target.
\end{remark}

\begin{remark}[The generalization principle: Arnold to Fay]
\label{rem:arnold-fay-generalization}
\index{Arnold relation!Fay generalization}
The Arnold relation (Theorem~\ref{thm:arnold-relations}), which governs the genus-$0$ bar differential, admits two distinct generalizations. Direction~(a): via clutching morphisms and the shadow obstruction tower $\Theta_A^{\leq r}$ (Definition~\ref{def:shadow-postnikov-tower}), one passes to the modular regime on stable curves, recovering the higher-genus bar complex of Part~\ref{part:bar-complex} (Remark~\ref{rem:five-pieces}). Direction~(b): via the Fay trisecant identity (Theorem~\ref{thm:fay}), one replaces the additive (logarithmic) propagator $\omega = dz/(z-w)$ by the elliptic (multiplicative) propagator built from the Weierstrass $\sigma$-function, entering the toroidal regime. The present chapter develops direction~(b): the systematic passage from logarithmic to elliptic propagators and its consequences for bar-cobar duality.
\end{remark}

\begin{remark}[Rational, trigonometric, elliptic: curve geometry]
\label{rem:rational-trig-elliptic}
\index{quantum group hierarchy!curve geometry}
\index{R-matrix!rational, trigonometric, elliptic}
The three quantum group families arise from the geometry of the underlying curve:
\begin{center}
\small
\begin{tabular}{llll}
\textbf{$R$-matrix type} & \textbf{Quantum group} &
 \textbf{Spectral parameter} & \textbf{Curve} \\ \hline
Rational
 & Yangian $Y(\fg)$
 & $u = z_1 - z_2$
 & $\mathbb{P}^1$ \\[2pt]
Trigonometric
 & Quantum loop $U_q(L\fg)$
 & $q = e^{2\pi i(z_1 - z_2)/\beta}$
 & $\mathbb{C}^*$ \\[2pt]
Elliptic
 & Elliptic QG $E_{q,p}(\fg)$
 & $u \in E_\tau$
 & $E_\tau$
\end{tabular}
\end{center}
The passage from rational to trigonometric to elliptic parallels additive $\to$ multiplicative $\to$ modular spectral parameter; this chapter develops the elliptic face.
\end{remark}

\begin{construction}[Elliptic shadow data]
\label{constr:elliptic-shadow-data}
\index{elliptic quantum group!shadow data}
Toroidal and elliptic quantum group algebras carry shadow data in the elliptic regime:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The elliptic propagator $K^{\mathrm{ell}}(z,w;\tau) = \vartheta_1(z-w;\tau)/\vartheta_1'(0;\tau)$ replaces the rational propagator $1/(z-w)$.
\item The Fay trisecant identity for $\vartheta_1$ is the genus-$1$ MC equation $D^{(1)}\Theta + \tfrac{1}{2}[\Theta^{(0)}, \Theta^{(0)}] + \kappa\,\omega_1 = 0$.
\item The Arnold relation $K_{12}K_{23} + K_{23}K_{31} + K_{31}K_{12} = 0$ (Fay identity) specializes the CYBE to the elliptic regime.
\end{enumerate}
\end{construction}

\section{Double affine setup}
\label{sec:double-affine}

\subsection{The toroidal algebra and its OPE}

\begin{definition}[Toroidal algebra]\label{def:toroidal}
\index{toroidal algebra|textbf}
\index{double affine algebra|textbf}
The \emph{toroidal algebra} (or double affine algebra) $U_{q,t}(\hat{\hat{\mathfrak{g}}})$ 
is generated by:
\begin{itemize}
\item Horizontal currents $x^\pm_{i,n}$, $\psi^\pm_{i,n}$ (affine in one direction)
\item Vertical currents $e_i(z)$, $f_i(z)$, $\psi_i(z)$ (affine in the other direction)
\end{itemize}
subject to:
\begin{enumerate}
\item \emph{Drinfeld--type relations} in each direction:
$[h_{i,m}, x^\pm_{j,n}] = \pm a_{ij} x^\pm_{j,m+n}$, \quad
$[x^+_{i,m}, x^-_{j,n}] = \delta_{ij} (\psi^+_{i,m+n} - \psi^-_{i,m+n})/(q_i - q_i^{-1})$
\item \emph{Cross relations} coupling horizontal and vertical:
$\psi_i(z) e_j(w) = g_{ij}(z/w) \, e_j(w) \psi_i(z)$
where $g_{ij}(u) = (u - q^{a_{ij}})/(u - q^{-a_{ij}})$
\item \emph{Serre relations} in both directions
\end{enumerate}
with two independent parameters $q$ and $t = q^k$. See Ginzburg--Kapranov--Vasserot
for the complete presentation.
\end{definition}

\begin{proposition}[Toroidal OPE \cite{FBZ04}; \ClaimStatusProvedElsewhere]\label{prop:toroidal-ope}
The OPE for toroidal currents involves both parameters:
\[
e_i(z) f_j(w) = \frac{\delta_{ij}}{(1 - q)(1 - t^{-1})} \cdot
\frac{\psi_i^+(w) - \psi_i^-(w)}{z - w} + \text{rational terms in } q, t
\]
\end{proposition}

\begin{proof}
We derive the OPE from the defining relations of Definition~\ref{def:toroidal}.

\emph{Step~1: Mode commutator.}
The Drinfeld-type relation (1) gives:
\[
[e_{i,m}, f_{j,n}] = \delta_{ij} \frac{\psi^+_{i,m+n} - \psi^-_{i,m+n}}{q_i - q_i^{-1}}.
\]
Form the generating functions $e_i(z) = \sum_m e_{i,m} z^{-m-1}$,
$f_j(w) = \sum_n f_{j,n} w^{-n-1}$, and
$\psi_i^\pm(w) = \sum_n \psi^\pm_{i,n} w^{-n}$.

\emph{Step~2: Extracting the OPE.}
Contracting the commutator against $z^{-m-1} w^{-n-1}$ and summing:
\[
e_i(z) f_j(w) - {:}e_i(z) f_j(w){:}
= \delta_{ij} \sum_{m} \frac{\psi^+_{i,m}(w) - \psi^-_{i,m}(w)}{q_i - q_i^{-1}} \cdot \frac{w^{-m}}{z - w}.
\]
For the toroidal algebra with parameters $q$ and $t = q^k$,
we have $q_i = q^{d_i}$ where $d_i = (\alpha_i, \alpha_i)/2$.
The singular part of the OPE is the residue at $z = w$:
\[
e_i(z) f_j(w) \sim \frac{\delta_{ij}}{q_i - q_i^{-1}} \cdot
\frac{\psi_i^+(w) - \psi_i^-(w)}{z - w}.
\]

\emph{Step~3: Two-parameter structure.}
The cross relation (2) introduces the second parameter.
From $\psi_i(z) e_j(w) = g_{ij}(z/w) \, e_j(w) \psi_i(z)$
with $g_{ij}(u) = (u - q^{a_{ij}})/(u - q^{-a_{ij}})$,
the normal ordering of $\psi$ against $e, f$ currents produces
corrections rational in both $q$ and $t$. Specifically, expanding
$1/(q_i - q_i^{-1}) = 1/((q^{d_i} - q^{-d_i}))$ and using
$t = q^k$ to express the central element as
$c = (1 - q)(1-t^{-1})/(q_i - q_i^{-1})$ (the standard Ding--Iohara
normalization). See~\cite{DI97} for the complete change-of-basis computation.
\end{proof}

\begin{conjecture}[Elliptic-curve toroidal realization; \ClaimStatusConjectured]\label{conj:toroidal-e1}
The toroidal algebra $U_{q,t}(\hat{\hat{\mathfrak{g}}})$ admits a
curve-based $\Eone$-chiral realization on the elliptic curve
$E_\tau$ (with modulus $\tau = \frac{\log t}{\log q}$).
\end{conjecture}

\begin{conjecture}[Double-affine surface-factorization realization;
\ClaimStatusConjectured]
\label{conj:toroidal-surface-factorization}
The same toroidal data should extend to a doubly-graded
surface-factorization or double-affine object on
$\bC^* \times \bC^*$, with one direction encoding the spectral
parameter and the other the elliptic coordinate.
(This is the toroidal/elliptic extension flank of
Conjecture~\ref{conj:master-infinite-generator}, not the standard
$W_\infty$/Yangian finite-packet lane.)
\end{conjecture}

\begin{remark}[Scope]
Conjecture~\ref{conj:toroidal-e1} is conjectural (\ClaimStatusConjectured): a complete proof requires verifying associativity of the $\Eone$-chiral product directly from the OPE relations, since the BD locality approach applies only to commutative chiral algebras. The $\bC^* \times \bC^*$ realization (Conjecture~\ref{conj:toroidal-surface-factorization}) is a separate surface-factorization problem within the MC4 elliptic/double-affine extension problem.

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~I (existence).
\end{remark}

\begin{remark}[Conjectural construction]
We describe the conjectural $\Eone$-chiral structure.

\emph{Step~1: $R$-matrix braiding.}
The cross relation (2) of Definition~\ref{def:toroidal} gives the
structure function $g_{ij}(z/w) = (z/w - q^{a_{ij}})/(z/w - q^{-a_{ij}})$.
Define the $R$-matrix-valued braiding on generating currents by
\[
\sigma_{12} \circ \mu(e_i(z), e_j(w))
= g_{ij}(z/w) \cdot \mu(e_j(w), e_i(z)).
\]
Since $g_{ij}(u)$ is a rational function with $g_{ij}(u) \neq 1$
for generic $q$ and $a_{ij} \neq 0$, the braiding is non-trivial:
the algebra is associative but not commutative, hence strictly $\Eone$.

\emph{Step~2: Associativity (gap).}
The $R$-matrix $R_{ij}(u) = g_{ij}(u) \cdot \mathrm{Id}$ satisfies
the Yang--Baxter equation trivially (being scalar-valued).
The genuine content of associativity lies in verifying that the
full matrix-valued OPE structure, including the Serre-type relations
of Definition~\ref{def:toroidal}, defines an algebra over $\chirAss$
(Definition~\ref{def:chiral-ass-operad}). This requires an explicit
verification that triple OPEs are consistent, which we do not
carry out here.

\emph{Step~3: Realization on $E_\tau$.}
Set $\tau = \log t / \log q$ and let $E_\tau = \bC^*/q^{\bZ}$.
The generating currents $e_i(z)$, $f_i(z)$, $\psi_i(z)$ are meromorphic
on $\bC^*$ with quasi-periodicity $e_i(qz) = q^{d_i} e_i(z)$
(from the grading), so they define sections of line bundles on $E_\tau$.
The OPE of Proposition~\ref{prop:toroidal-ope} has poles at
$z/w \in q^{\bZ}$, which descend to a single point on $E_\tau$.
This defines a candidate $\Eone$-chiral algebra structure on $E_\tau$,
pending verification of Step~2.

\emph{Step~4: Surface-factorization horizon on $\bC^* \times \bC^*$.}
The horizontal modes $x^\pm_{i,n}$ depend on the spectral
parameter $u$ and the vertical modes $e_i(z)$ depend on $z$.
Together they give fields on $\bC^*_u \times \bC^*_z$ with the
two independent gradings (by horizontal and vertical mode number)
providing the doubly-graded structure. This belongs to a separate
conjectural surface-factorization or double-affine track, not
automatically a
curve-based $\Eone$-chiral algebra. A correct formulation would
require a bona fide two-parameter factorization framework.

Conditional on Step~2 (i.e., the verification that the toroidal OPE
defines an associative $\chirAss$-algebra structure, which requires
checking consistency of triple OPEs with the Serre-type relations), the
$\Eone$-chiral Koszul duality framework
(Theorem~\ref{thm:e1-chiral-koszul-duality}) applies to the
elliptic-curve realization of Conjecture~\ref{conj:toroidal-e1}. The
$\bC^* \times \bC^*$ surface track belongs instead to
Conjecture~\ref{conj:toroidal-surface-factorization}.
\end{remark}


\subsection{Koszul dual of the toroidal algebra}

\begin{conjecture}[Toroidal Koszul dual; \ClaimStatusConjectured]
\label{conj:toroidal-koszul-dual}
\index{toroidal algebra!Koszul dual}
The $\Eone$-chiral Koszul dual of the toroidal algebra
$U_{q,t}(\hat{\hat{\mathfrak{g}}})$ is isomorphic to
$U_{q^{-1},t^{-1}}(\hat{\hat{\mathfrak{g}}})$,
the toroidal algebra with inverted parameters.
(Contributing to the toroidal/elliptic extension flank of
Conjecture~\ref{conj:master-infinite-generator}.)
\end{conjecture}

\begin{remark}[Evidence]\label{rem:toroidal-koszul-evidence}
Conditional on Conjecture~\ref{conj:toroidal-e1}, the evidence is threefold:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{RTT presentation.} By $\Eone$-chiral Koszul duality (Theorem~\ref{thm:e1-chiral-koszul-duality}), the dual has $R$-matrix $R(u;q,t)^{-1} = R(u;q^{-1},t^{-1})$ (Ding--Iohara inversion; cf.\ Theorem~\ref{thm:yangian-koszul-dual}).
\item \emph{Affine degeneration.} In the limit $t \to 0$, $U_{q,t}(\hat{\hat{\mathfrak{g}}}) \to U_q(\hat{\mathfrak{g}})$ and the dual reduces to $U_{q^{-1}}(\hat{\mathfrak{g}})$, consistent with Theorem~\ref{thm:km-quantum-groups}.
\item \emph{Central charge complementarity.} The inversion $q \to q^{-1}$ sends $\tau \to -\tau$, reversing the complex structure of $E_\tau$, the elliptic analogue of Verdier duality (Theorem~\ref{thm:bar-cobar-verdier}).
\end{enumerate}
The Fay identity (Proposition~\ref{prop:fay-implies-d-squared}) serves as the elliptic Arnold relation. The universal MC class predicts $\Theta_{U_{q,t}} + \Theta_{U_{q^{-1},t^{-1}}} = 0$.

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~II (equivalence).
\end{remark}

\subsection{Connection to the three main theorems}

\begin{remark}[Toroidal three theorems]
\label{rem:toroidal-three-theorems}
\index{three theorems!toroidal}
Conditional on Conjecture~\ref{conj:toroidal-e1}, the expected forms are:
\emph{Theorem~A}: $\bar{B}^{\mathrm{ell}}(U_{q,t})$ computes the Koszul dual coalgebra (nilpotency via Proposition~\ref{prop:fay-implies-d-squared}).
\emph{Theorem~B}: $\Omega(\bar{B}(U_{q,t})) \xrightarrow{\sim} U_{q,t}$ by the rational spectral sequence with elliptic corrections (Theorem~\ref{thm:elliptic-vs-rational}).
\emph{Theorem~C}: $\mathrm{obs}_g(U_{q,t}) + \mathrm{obs}_g(U_{q^{-1},t^{-1}})$ controlled by $H^*$ of a framed moduli space (the $\Eone$ replacement for $\overline{\mathcal{M}}_g$; cf.\ Remark~\ref{rem:yangian-three-theorems}).
The universal MC class $\Theta_{U_{q,t}}$ should govern the genus expansion, with $(q,t) \mapsto (q^{-1},t^{-1})$ reflected in Verdier duality.
\end{remark}

\begin{remark}[Lattice evidence for toroidal genus theory]
\label{rem:toroidal-lattice-evidence}
\index{lattice vertex algebra!genus-1 evidence for toroidal}
The curvature-braiding orthogonality theorem for quantum lattice VOAs
(Theorem~\ref{thm:lattice:curvature-braiding-orthogonal}) provides
structural evidence for the toroidal case. For the lattice VOA
$V_\Lambda$, the genus-$1$ curvature is
$\kappa(V_\Lambda) = \operatorname{rank}(\Lambda)$, so
$\kappa(V_\Lambda) = 0$ at rank~$0$ and
$\kappa(V_\Lambda) = 24$ at rank~$24$ for the Leech/Niemeier case in
the landscape census. This curvature lives
entirely in the Cartan (Heisenberg) sector and is independent of the
deformation cocycle $\varepsilon_{N,q}$. The same census places lattice
VOAs in class~G with $r_{\max} = 2$; equivalently
$S_4(V_\Lambda) = 0$ and
$\Delta(V_\Lambda) = 8\,\kappa(V_\Lambda)\,S_4(V_\Lambda) = 0$.
The toroidal algebra $U_{q,t}(\hat{\hat{\fg}})$
has a similar double-loop structure: the inner loop ($\hat{\fg}$) is the
Cartan analog, while the outer loop (the second affinization) provides
the braiding. The orthogonality principle predicts that the toroidal
genus-$1$ curvature should be controlled by the inner-loop data alone,
with the dynamical parameter $\lambda \in H^1(E_\tau)$ entering the
braiding axis rather than the modular axis. The dynamical YBE for
$R(u, \lambda)$ would then be the toroidal analog of the modified
Arnold relation at genus~$1$, with the dynamical shift
$\lambda \to \lambda - h^{(i)}$ replacing the B-cycle monodromy
correction.
\end{remark}

\section{Elliptic quantum groups}
\label{sec:elliptic-quantum}

\subsection{Felder's elliptic quantum group}

\begin{definition}[Elliptic quantum group]\label{def:elliptic-quantum}
\index{elliptic quantum group|textbf}
The \emph{elliptic quantum group} $E_{q,p}(\mathfrak{g})$ (Felder) is defined by:
\begin{itemize}
\item The dynamical R-matrix $R(u, \lambda)$ depending on spectral parameter $u$ 
and dynamical parameter $\lambda$.
\item The RLL relations:
\[
R(u-v, \lambda) L_1(u, \lambda) L_2(v, \lambda - h^{(1)}) = L_2(v, \lambda) L_1(u, \lambda - h^{(2)}) R(u-v, \lambda)
\]
\end{itemize}
\end{definition}

\begin{definition}[Elliptic R-matrix]\label{def:elliptic-r}
The elliptic R-matrix for $\mathfrak{sl}_2$ is:
\[
R(u, \lambda) = \begin{pmatrix}
a(u) & 0 & 0 & 0 \\
0 & b(u, \lambda) & c(u, \lambda) & 0 \\
0 & c(u, -\lambda) & b(u, -\lambda) & 0 \\
0 & 0 & 0 & a(u)
\end{pmatrix}
\]
where $a(u), b(u, \lambda), c(u, \lambda)$ are expressed via theta functions:
\begin{align*}
a(u) &= \frac{\theta(u + \eta)}{\theta(\eta)} \\
b(u, \lambda) &= \frac{\theta(u)\theta(\lambda + \eta)}{\theta(\eta)\theta(\lambda)} \\
c(u, \lambda) &= \frac{\theta(u + \lambda)\theta(\eta)}{\theta(\lambda)\theta(u + \eta)}
\end{align*}
\end{definition}


\begin{remark}[Elliptic quantum groups and bar complex]
\label{rem:elliptic-qg-bar}
\index{elliptic quantum group!bar complex}
We expect (\ClaimStatusConjectured, conditional on Conjecture~\ref{conj:toroidal-e1}):
(i)~$\barB(U_{q,t})$ on $E_\tau$ computes the chiral coalgebra $E_{q,p}(\mathfrak{g})$ (elliptic Kazhdan--Lusztig);
(ii)~the dynamical parameter $\lambda$ (Definition~\ref{def:elliptic-quantum}) is the B-cycle monodromy of the elliptic propagator (elliptic analogue of $k \to k + h^\vee$);
(iii)~the dynamical YBE for $R(u,\lambda)$ is the elliptic deformation of $d^2 = 0$ (Proposition~\ref{prop:fay-implies-d-squared}), with the dynamical parameter from $H^1(E_\tau) \neq 0$.
\end{remark}

\section{Elliptic R-matrices and theta functions}
\label{sec:elliptic-r-theta}

\subsection{Theta function identities}

\begin{definition}[Jacobi theta function]\label{def:theta}
The Jacobi theta function is:
\[
\theta(u | \tau) = \sum_{n \in \bZ} (-1)^n e^{\pi i \tau n(n-1) + 2\pi i n u} =
(e^{2\pi iu}; p)_\infty (p e^{-2\pi iu}; p)_\infty (p; p)_\infty
\]
where $p = e^{2\pi i \tau}$ and $(a; q)_\infty = \prod_{n \geq 0}(1 - aq^n)$.
\end{definition}

\begin{theorem}[Fay identity at genus 1 \cite{Fay73}; \ClaimStatusProvedElsewhere]\label{thm:fay}
\index{Fay trisecant identity|textbf}
For any four points $u_1, u_2, u_3, u_4$ on an elliptic curve $E_\tau$, the theta function
satisfies the Fay trisecant identity:
\[
\theta(u_1 - u_2)\,\theta(u_3 - u_4) - \theta(u_1 - u_3)\,\theta(u_2 - u_4) + \theta(u_1 - u_4)\,\theta(u_2 - u_3) = 0
\]
This is a \emph{bilinear} identity (each term is a product of two theta functions), which at genus~1 is the degenerate case of the general Fay trisecant identity on higher-genus curves. The identity is equivalent to the Riemann addition formula and reduces to the Ptolemy relation $\sin(\alpha-\beta)\sin(\gamma-\delta) - \sin(\alpha-\gamma)\sin(\beta-\delta) + \sin(\alpha-\delta)\sin(\beta-\gamma) = 0$ in the rational limit $\tau \to i\infty$.

This identity underlies the Yang--Baxter equation for elliptic R-matrices:
the star-triangle relation is a consequence of the Fay identity applied to the
structure functions of the elliptic algebra.
\end{theorem}


\subsection{Fay identity and bar nilpotency}

\begin{proposition}[Fay identity implies elliptic \texorpdfstring{$d^2 = 0$}{d2 = 0};
\ClaimStatusProvedHere]\label{prop:fay-implies-d-squared}
\index{Fay trisecant identity!and bar nilpotency}
On $\overline{C}_3(E_\tau)$, the elliptic bar differential satisfies
$d^2 = 0$. The key algebraic input is the Fay trisecant identity
(Theorem~\ref{thm:fay}), which plays the role of the Arnold relation
in the rational case (Theorem~\ref{thm:bar-nilpotency-complete}).
\end{proposition}

\begin{proof}
The elliptic bar differential on degree-$2$ elements uses the
propagator $\eta_{ij}^{\mathrm{ell}} = d\log\theta_1(z_i - z_j
| \tau)$. The computation of $d^2$ on a degree-$1$ element
$[a] \otimes 1$ produces terms on $\overline{C}_3(E_\tau)$ involving
the $2$-form $\eta_{12}^{\mathrm{ell}} \wedge \eta_{23}^{\mathrm{ell}}
+ \eta_{23}^{\mathrm{ell}} \wedge \eta_{31}^{\mathrm{ell}}
+ \eta_{31}^{\mathrm{ell}} \wedge \eta_{12}^{\mathrm{ell}}$,
exactly as in the rational case (cf.\
\S\ref{sec:bar-nilpotency-nine-terms-complete}).

The rational Arnold relation $\eta_{12} \wedge \eta_{23}
+ \eta_{23} \wedge \eta_{31} + \eta_{31} \wedge \eta_{12} = 0$
(where $\eta_{ij} = d\log(z_i - z_j)$) is a consequence of
the partial fraction identity
$(z_1 - z_2)^{-1}(z_2 - z_3)^{-1} + \text{cyclic} = 0$.

The elliptic replacement for $(z_i-z_j)^{-1}$ is
$\zeta_\tau(z_i - z_j) := \partial_z \log\theta_1(z_i - z_j|\tau)$,
the Weierstrass $\zeta$-function on $E_\tau$. The corresponding
three-term identity is
\begin{equation}\label{eq:elliptic-arnold}
d\zeta_\tau(z_1{-}z_2) \wedge d\zeta_\tau(z_2{-}z_3)
+ d\zeta_\tau(z_2{-}z_3) \wedge d\zeta_\tau(z_3{-}z_1)
+ d\zeta_\tau(z_3{-}z_1) \wedge d\zeta_\tau(z_1{-}z_2) = 0.
\end{equation}

This is the differential-form shadow of the Fay identity
(Theorem~\ref{thm:fay}). Differentiate
\[
\theta(u_1{-}u_2)\,\theta(u_3{-}u_4) -
\theta(u_1{-}u_3)\,\theta(u_2{-}u_4) +
\theta(u_1{-}u_4)\,\theta(u_2{-}u_3) = 0
\]
with respect to $u_1$ and $u_4$, then set $u_4 = u_1$. The resulting
trisecant consequence is
\begin{multline*}
\zeta_\tau(u_1{-}u_2)\,\zeta_\tau(u_2{-}u_3)
+ \zeta_\tau(u_2{-}u_3)\,\zeta_\tau(u_3{-}u_1)
+ \zeta_\tau(u_3{-}u_1)\,\zeta_\tau(u_1{-}u_2) \\
= \wp_\tau(u_1{-}u_2) + \wp_\tau(u_2{-}u_3) + \wp_\tau(u_3{-}u_1)
\end{multline*}
where $\wp_\tau = -\zeta_\tau'$ is the Weierstrass $\wp$-function.
Now take exterior derivatives in the difference variables. Each
$\wp_\tau(z_i-z_j)$ depends on a single difference, so the mixed wedges
on the right vanish or cancel pairwise. The left-hand side is then
exactly~\eqref{eq:elliptic-arnold}.

The remaining terms in $d^2$ (involving OPE data of the chiral
algebra $\cA$) cancel by the same mechanism as in the rational case:
the bar differential decomposes as $d = d_{\mathrm{local}} +
d_{\mathrm{global}}$, where $d_{\mathrm{local}}^2 = 0$ by the OPE
associativity of $\cA$, and the cross-terms $d_{\mathrm{local}} \circ
d_{\mathrm{global}} + d_{\mathrm{global}} \circ d_{\mathrm{local}} = 0$
by the compatibility of the OPE with the propagator (which holds for
both the rational and elliptic propagators, since the residue at a
simple pole is the same: $\Res_{z=0} \zeta_\tau(z)\,dz = 1$).
\end{proof}

\begin{remark}[Rational limit]\label{rem:fay-to-arnold}
In the rational limit $\tau \to i\infty$, the theta function
$\theta_1(z|\tau) \to 2\sin(\pi z) \to 2\pi z$ (for $|z|$ small),
so $\zeta_\tau(z) \to 1/z$ and $\wp_\tau(z) \to 1/z^2$.
The identity~\eqref{eq:elliptic-arnold} reduces to the Arnold relation
$\eta_{12} \wedge \eta_{23} + \eta_{23} \wedge \eta_{31} +
\eta_{31} \wedge \eta_{12} = 0$
(Theorem~\ref{thm:arnold-relations}), and the
bar nilpotency reduces to
Theorem~\ref{thm:bar-nilpotency-complete}.
\end{remark}


\subsection{Bar complex with theta functions}

\begin{construction}[Elliptic bar complex]\label{constr:elliptic-bar}
The bar complex of an elliptic chiral algebra incorporates theta functions:

\emph{Forms.} Replace $d\log(z_1 - z_2)$ with:
\[
\eta_{12} = d\log\theta(z_1 - z_2 | \tau)
\]
the logarithmic derivative of theta.

\emph{Differential.} The residue is computed at the zeros of $\theta$:
\[
d_{\text{res}}([a|b] \otimes \eta_{12}) = \sum_{\theta(z_0) = 0} \Res_{z_1 = z_0 + z_2}[\cdots]
\]
The zeros of $\theta(u|\tau)$ are at $u = m + n\tau$ for $m, n \in \bZ$ (the lattice points).
\end{construction}

\begin{theorem}[Elliptic vs rational homology; \ClaimStatusProvedHere]\label{thm:elliptic-vs-rational}
Let $\cA$ be a chiral algebra of central charge $c$ on an elliptic curve $E_\tau$.
The homology of the elliptic bar complex admits a decomposition:
\[
H_n(\B^{\mathrm{ell}}(\cA)) \;\cong\; H_n(\B^{\mathrm{rat}}(\cA))
\;\oplus\; \bigoplus_{k \geq 1} \mathcal{E}^{(k)}_n(\cA, \tau)
\]
where the elliptic corrections $\mathcal{E}^{(k)}_n(\cA, \tau)$
are $\cA$-modules whose dependence on $\tau$ is through
(quasi-)modular forms. Specifically:
\begin{enumerate}[label=(\roman*)]
\item The leading correction $\mathcal{E}^{(1)}_n$ is
proportional to $E_2(\tau)$, the weight-2 quasi-modular
Eisenstein series, arising from the regularization of
the elliptic propagator $\partial_z \log\theta(z|\tau)$
relative to the rational propagator $1/z$
(cf.\ Construction~\ref{constr:elliptic-bar}).
\item Higher corrections $\mathcal{E}^{(k)}_n$ for $k \geq 2$
lie in the space of modular forms $M_{2k}(\mathrm{SL}_2(\bZ))$
of weight $2k$; the first truly modular correction is an
$E_4(\tau)$-coefficient.
\item The conformal dimension $h$ of the states entering the
bar complex constrains the weights: a state of dimension $h$
contributes to $\mathcal{E}^{(k)}_n$ only for $k \leq h + n$.
\item At the rational limit $\tau \to i\infty$ (i.e., $q = e^{2\pi i\tau} \to 0$),
the Eisenstein series $E_{2k}(\tau) \to 1$ and all corrections
degenerate to constants, recovering
$H_n(\B^{\mathrm{rat}}(\cA))$ up to scalar renormalization.
\end{enumerate}
For the Heisenberg algebra ($c = 1$), the corrections reduce to the
Eisenstein series hierarchy computed in
\S\ref{sec:heisenberg-genus-expansion-eisenstein}.
\end{theorem}

\begin{proof}
We construct the decomposition via a perturbative spectral sequence
comparing the elliptic and rational bar differentials.

\emph{Step~1 (Propagator decomposition).}
The elliptic bar complex (Construction~\ref{constr:elliptic-bar})
uses the propagator $\eta_{ij}^{\mathrm{ell}} = d\log\theta_1(z_i -
z_j|\tau)$, while the rational bar complex uses $\eta_{ij}^{\mathrm{rat}}
= d\log(z_i - z_j)$. Near $z_i = z_j$, both propagators have the same
simple pole with residue~$1$, so their difference $\delta_{ij}(\tau) :=
\eta_{ij}^{\mathrm{ell}} - \eta_{ij}^{\mathrm{rat}}$ is a regular
$1$-form. The classical expansion of the Weierstrass $\zeta$-function
$\zeta(z;\Lambda_\tau)$ in terms of the Eisenstein--Weierstrass series
$G_{2k}(\tau)$ gives the Laurent expansion:

\[
\partial_z\log\theta_1(z|\tau)
\;=\; \frac{1}{z} + \sum_{k=1}^{\infty} c_k(\tau)\,z^{2k-1},
\]
where the correction coefficients $c_k(\tau)$ are expressed in terms
of Eisenstein series via $G_{2k}(\tau) = 2\zeta_{\mathrm{R}}(2k)\,
E_{2k}(\tau)$:
\begin{itemize}
\item $c_1(\tau) = -\tfrac{\pi^2}{3}E_2(\tau) \in
\widetilde{M}_2(\mathrm{SL}_2(\bZ))$ (quasi-modular, weight~$2$),
since $c_1 = -2\eta_1$ where
$\eta_1 = \zeta(1/2;\Lambda_\tau) = \tfrac{\pi^2}{6}E_2(\tau)$;
\item $c_k(\tau) = -G_{2k}(\tau) \in M_{2k}(\mathrm{SL}_2(\bZ))$
for $k \geq 2$ (holomorphic modular forms).
\end{itemize}
The expansion converges absolutely for $|z| < \min_{\omega \in
\Lambda_\tau \setminus\{0\}} |\omega|$.

\emph{Step~2 (Correction-order filtration).}
Define the \emph{correction-order filtration}
$\mathcal{F}^p \bar{B}^{\mathrm{ell}}_n(\cA)$ by
declaring that an element has filtration degree $\geq p$ if it arises
from at least $p$ insertions of the regular correction terms
$\{c_k(\tau)\,z^{2k-1}\}_{k \geq 1}$ in the propagator expansion.
Equivalently, replace each propagator by $1/z + t\cdot(c_1 z + c_2 z^3
+ \cdots)$ and expand in powers of the formal parameter~$t$; then
$\mathcal{F}^p$ consists of terms of order~$\geq t^p$.

Since the bar differential $d^{\mathrm{ell}}$ at degree~$n$
involves at most $n$ propagator factors, we have $\mathcal{F}^{n+1}
\bar{B}^{\mathrm{ell}}_n = 0$. The filtration is compatible
with the differential: $d^{\mathrm{ell}}(\mathcal{F}^p) \subset
\mathcal{F}^p$ (inserting the bar differential does not decrease
the number of correction insertions).

\emph{Step~3 (Spectral sequence: $E_0$ and $E_1$ pages).}
The associated graded $\mathrm{gr}^0_{\mathcal{F}}
\bar{B}^{\mathrm{ell}}(\cA)$ is the bar complex computed using only the
singular part $1/z$ of the propagator. Since the residue extraction
in the bar differential (which encodes the OPE data of~$\cA$) depends
only on the polar part, the differential on $\mathrm{gr}^0$ coincides
with the rational bar differential $d^{\mathrm{rat}}$. Thus:
\[
E_1^{0,n} = H_n(\bar{B}^{\mathrm{rat}}(\cA)).
\]
More generally, $E_1^{p,n} = H_n(\bar{B}^{\mathrm{rat}}(\cA)) \otimes
\mathrm{Sym}^p_{\geq 1}\{c_k(\tau)\}$, where the symmetric product is
taken over all propagator correction coefficients contributing total
weight~$p$.

\emph{Step~4 (Modular structure via Zhu's theorem).}
The differential $d_r \colon E_r^{p,n} \to E_r^{p+r,n+1}$ on the
$r$-th page arises from the interaction of $r$ correction insertions
with the bar differential. By Zhu's modular invariance
theorem~\cite{Zhu96}, the $n$-point genus-$1$ correlation functions
$\langle V_1(z_1) \cdots V_n(z_n) \rangle_{E_\tau}$ of a rational
vertex algebra $\cA$ transform as components of a vector-valued modular
form for $\mathrm{SL}_2(\bZ)$. Since the bar complex at degree~$n$ is
built from such correlation functions composed with the propagator form,
and the correction coefficients $c_k(\tau)$ are themselves
(quasi-)modular, the differentials $d_r$ respect the modular weight
grading. Consequently, the $E_\infty$ terms inherit a weight
decomposition from the ring $\widetilde{M}_*(\mathrm{SL}_2(\bZ))$
of quasi-modular forms.

\emph{Step~5 (Convergence and splitting).}
The spectral sequence converges because the filtration is bounded:
$\mathcal{F}^{n+1}\bar{B}^{\mathrm{ell}}_n = 0$ at each bar
degree~$n$. At convergence, $H_n(\bar{B}^{\mathrm{ell}}(\cA))$
admits the filtration
\[
0 = \mathcal{F}^{n+1} H_n \subset \mathcal{F}^n H_n \subset \cdots
\subset \mathcal{F}^1 H_n \subset \mathcal{F}^0 H_n
= H_n(\bar{B}^{\mathrm{ell}}(\cA))
\]
with successive quotients $\mathcal{E}^{(k)}_n := E_\infty^{k,n}$.
The filtration \emph{splits}: the modular weight provides a grading
on the coefficient ring (quasi-modular forms of different weights are
linearly independent over~$\bC$), and the $E_\infty$ terms in
different weights cannot be related by extensions. We therefore
obtain the direct sum decomposition
$H_n(\bar{B}^{\mathrm{ell}}(\cA)) \cong H_n(\bar{B}^{\mathrm{rat}}(\cA))
\oplus \bigoplus_{k \geq 1} \mathcal{E}^{(k)}_n(\cA, \tau)$
as claimed.

Properties~(i)--(iv) now follow from the structure of the correction
coefficients:
\begin{enumerate}[label=(\roman*)]
\item The leading correction involves $c_1(\tau) = -(\pi^2/3)\,E_2(\tau)$
(quasi-modular, weight~$2$).
\item Higher corrections involve products of
$c_k(\tau) \in M_{2k}(\mathrm{SL}_2(\bZ))$ for $k \geq 2$.
\item A bar element of degree~$n$ involves at most $n$ propagator
factors; a state of conformal dimension~$h$ constrains the Laurent
order of each propagator insertion to $\leq 2h - 1$, giving the bound
$\mathcal{E}^{(k)}_n = 0$ for $k > h + n$.
\item As $\tau \to i\infty$: $q \to 0$ and $E_{2k}(\tau) \to 1$, so all
corrections reduce to constants, recovering $H_n(\bar{B}^{\mathrm{rat}}(\cA))$
up to renormalization.
\end{enumerate}

\emph{Verification for the Heisenberg algebra.}
For $\cA = \mathcal{H}$ ($c = 1$), the genus-$1$ two-point function is
$\langle a(z_1)a(z_2)\rangle_{E_\tau} = \kappa\,G_\tau(z_1 - z_2)$
with $G_\tau(z) = \zeta_\tau(z) - (\pi^2 E_2(\tau)/3)\,z$
(Theorem~\ref{thm:heisenberg-genus-one-complete}). The leading
correction $\mathcal{E}^{(1)}_n \propto E_2(\tau)$ arises from the
$c_1$ term. The complete Eisenstein hierarchy of
\S\ref{sec:heisenberg-genus-expansion-eisenstein} gives
$\mathcal{E}^{(k)}_n \propto E_{2k}(\tau)$, confirming the general
pattern.
\end{proof}

\begin{remark}[Scope]
The proof assembles three ingredients:
(i)~the Laurent expansion of the Weierstrass $\zeta$-function in
terms of Eisenstein series (\ClaimStatusProvedElsewhere, classical);
(ii)~the convergence of the correction-order spectral sequence
(bounded filtration at each bar degree); and
(iii)~Zhu's modular invariance theorem for genus-$1$ $n$-point
functions of rational vertex algebras~\cite{Zhu96}
(\ClaimStatusProvedElsewhere). The combination and the identification
of the splitting mechanism (Step~5) are new to this work.
The Heisenberg verification uses the explicit computations of
\S\ref{sec:heisenberg-genus-expansion-eisenstein}.
\end{remark}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EXPLICIT COMPUTATIONS: ELLIPTIC BAR, DYNAMICAL YBE, SHUFFLE, COMPARISON
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Explicit elliptic bar complex for the Heisenberg algebra}
\label{sec:elliptic-bar-heisenberg}
\index{bar complex!elliptic Heisenberg|textbf}
\index{Heisenberg algebra!elliptic bar complex}

\subsection{Bar elements and the elliptic propagator}
\label{subsec:elliptic-bar-elements}

We work on $E_\tau = \bC / (\bZ + \tau\bZ)$ with the elliptic
propagator
\begin{equation}\label{eq:ell-propagator}
\eta_{ij}^{\mathrm{ell}}
= d\log\theta_1(z_i - z_j \,|\, \tau)
= \zeta_\tau(z_i - z_j)\,(dz_i - dz_j),
\end{equation}
where $\zeta_\tau(z) = \partial_z \log\theta_1(z|\tau)$ is the
Weierstrass zeta function on $E_\tau$.

\begin{computation}[Degree-1 bar elements]\label{comp:ell-bar-deg1}
\index{bar complex!elliptic!degree 1}
In bar degree~$1$, the generators of $\B^{\mathrm{ell}}_1(\cH_\kappa)$
are:
\[
[a_m] \otimes 1 \in \B^{\mathrm{ell}}_1(\cH_\kappa), \quad m \in \bZ,
\]
where $a_m$ denotes the mode of the Heisenberg current $a(z) = \sum_m a_m z^{-m-1}$.
The bar differential on degree-$1$ elements is:
\[
d^{\mathrm{ell}}([a_m] \otimes 1) = 0,
\]
since the Heisenberg algebra has trivial unary OPE
($a_{(n)}a = 0$ for $n \geq 1$ except $a_{(1)}a = \kappa$, and
the residue extraction on a single element yields zero).
This is identical to the rational case.
\end{computation}

\begin{computation}[Degree-2 bar elements and the elliptic differential]
\label{comp:ell-bar-deg2}
\index{bar complex!elliptic!degree 2}
In bar degree~$2$, the generators are:
\[
[a_m | a_n] \otimes \eta_{12}^{\mathrm{ell}}
\in \B^{\mathrm{ell}}_2(\cH_\kappa),
\]
where $\eta_{12}^{\mathrm{ell}} = \zeta_\tau(z_1 - z_2)\,(dz_1 - dz_2)$.
The bar differential acts by residue extraction:
\begin{align}\label{eq:ell-bar-diff-deg2}
d^{\mathrm{ell}}([a_m | a_n] \otimes \eta_{12}^{\mathrm{ell}})
&= \Res_{z_1 = z_2}\Bigl[
a_m(z_1)\,a_n(z_2)\,\eta_{12}^{\mathrm{ell}}
\Bigr] \notag \\
&= \Res_{\epsilon = 0}\left[
\frac{\kappa}{\epsilon^2}\,
\zeta_\tau(\epsilon)\,d\epsilon
\right] \cdot z_2^{-m-n-2}\,dz_2,
\end{align}
where $\epsilon = z_1 - z_2$. We use the Laurent expansion of
$\zeta_\tau$ (established in the proof of
Theorem~\ref{thm:elliptic-vs-rational}, Step~1):
\begin{equation}\label{eq:zeta-laurent}
\zeta_\tau(\epsilon)
= \frac{1}{\epsilon}
- \frac{\pi^2}{3}\,E_2(\tau)\,\epsilon
- \frac{\pi^4}{45}\,E_4(\tau)\,\epsilon^3
- \frac{2\pi^6}{945}\,E_6(\tau)\,\epsilon^5
- \cdots
\end{equation}
Substituting into the residue:
\begin{align}\label{eq:ell-residue-expansion}
\Res_{\epsilon = 0}\left[
\frac{\kappa}{\epsilon^2}\,
\zeta_\tau(\epsilon)\,d\epsilon
\right]
&= \Res_{\epsilon = 0}\left[
\frac{\kappa}{\epsilon^2}\left(
\frac{1}{\epsilon}
- \frac{\pi^2}{3}\,E_2(\tau)\,\epsilon
- \cdots
\right) d\epsilon
\right] \notag \\
&= \Res_{\epsilon = 0}\left[
\frac{\kappa}{\epsilon^3}
- \frac{\kappa\pi^2}{3}\,E_2(\tau)\,\frac{1}{\epsilon}
- \cdots
\right] d\epsilon \notag \\
&= -\frac{\kappa\pi^2}{3}\,E_2(\tau).
\end{align}
The $1/\epsilon^3$ term has zero residue; the first nonzero
contribution is the $E_2(\tau)$ term. In the rational case
($\zeta_\tau(\epsilon) \to 1/\epsilon$), the residue of
$\kappa\epsilon^{-3}\,d\epsilon$ vanishes, so the rational
bar differential on this element is zero. The
\emph{entire degree-$2$ bar differential is the elliptic
correction}:
\begin{equation}\label{eq:ell-bar-diff-result}
d^{\mathrm{ell}}([a_m | a_n] \otimes \eta_{12}^{\mathrm{ell}})
= -\frac{\kappa\pi^2}{3}\,E_2(\tau)
\cdot z_2^{-m-n-2}\,dz_2.
\end{equation}
\end{computation}

\begin{computation}[Degree-2 curvature]\label{comp:ell-curvature}
\index{curvature!elliptic bar complex}
The elliptic bar complex of $\cH_\kappa$ has curvature
element $m_0^{\mathrm{ell}} \in \B^{\mathrm{ell}}_0(\cH_\kappa)$.
From the genus-$1$ propagator
(Theorem~\ref{thm:heisenberg-genus-one-complete}), the
two-point function on $E_\tau$ is $\langle a(z_1)\,a(z_2)
\rangle_{E_\tau} = \kappa\,G_\tau(z_1 - z_2)$, where
$G_\tau(z) = \zeta_\tau(z) - (\pi^2 E_2(\tau)/3)\,z$.
The curvature arises from the failure of double periodicity
(cf.\ the proof of
Theorem~\ref{thm:heisenberg-genus2-obstruction}):
\begin{equation}\label{eq:ell-curvature}
m_0^{\mathrm{ell}}
= \kappa \cdot \frac{\pi^2 E_2(\tau)}{3}.
\end{equation}
Expanding in the nome $q = e^{2\pi i \tau}$:
\begin{equation}\label{eq:ell-curvature-q}
m_0^{\mathrm{ell}}
= \frac{\kappa\pi^2}{3}\bigl(
1 - 24q - 72q^2 - 96q^3 - \cdots
\bigr).
\end{equation}
At the rational limit $\tau \to i\infty$ ($q \to 0$),
$E_2(\tau) \to 1$ and $m_0^{\mathrm{ell}} \to
\kappa\pi^2/3$, recovering the rational curvature
(up to the normalization convention for the propagator
on $\bC$ versus $E_\tau$; on $\bC$ the propagator
$1/z$ has no $B$-cycle and hence $m_0^{\mathrm{rat}} = 0$).
\end{computation}

\subsection{Comparison table: elliptic versus rational}
\label{subsec:ell-vs-rat-table}

\begin{table}[ht]
\centering
\caption{Elliptic versus rational bar differentials
for $\cH_\kappa$ at low degrees}
\label{tab:ell-vs-rat-bar}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Degree} & \textbf{Rational $d^{\mathrm{rat}}$}
& \textbf{Elliptic $d^{\mathrm{ell}}$}
& \textbf{Correction} \\
\hline
$1$ & $0$ & $0$ & --- \\
\hline
$2$ & $0$ & $-\frac{\kappa\pi^2}{3}\,E_2(\tau)$
& $E_2(\tau)$ (quasi-modular, wt~$2$) \\
\hline
$3$ & $0$ & $-\frac{\kappa\pi^4}{45}\,E_4(\tau)$
& $E_4(\tau)$ (modular, wt~$4$) \\
\hline
$4$ & $0$ & $-\frac{2\kappa\pi^6}{945}\,E_6(\tau)$
& $E_6(\tau)$ (modular, wt~$6$) \\
\hline
$5$ & $0$ & $-\frac{\kappa\pi^8}{4725}\,E_8(\tau)$
& $E_8(\tau)$ (modular, wt~$8$) \\
\hline
$6$ & $0$ & $-\frac{2\kappa\pi^{10}}{93555}\,E_{10}(\tau)$
& $E_{10}(\tau)$ (modular, wt~$10$) \\
\hline
$7$ & $0$ & $-\frac{1382\kappa\pi^{12}}{638512875}\,E_{12}(\tau)$
& $E_{12}(\tau)$ (modular, wt~$12$) \\
\hline
$8$ & $0$ & $-\frac{4\kappa\pi^{14}}{18243225}\,E_{14}(\tau)$
& $E_{14}(\tau)$ (modular, wt~$14$) \\
\hline
\textbf{General $n$}
& $0$ & $-\kappa \cdot \tfrac{2^{2n-2}|B_{2n-2}|}{(2n-2)!}
 \cdot \pi^{2n-2}\,E_{2n-2}(\tau)$
& $E_{2n-2}(\tau)$ (wt~$2n{-}2$) \\
\hline
\end{tabular}
\end{table}

\noindent
The vanishing of the rational bar differential at all degrees
reflects that the Heisenberg algebra on $\bC$ (genus~$0$)
has no curvature ($m_0^{\mathrm{rat}} = 0$): the propagator
$1/z$ is strictly periodic on $\bC$ (there is no $B$-cycle).
On the elliptic curve $E_\tau$, the $B$-cycle monodromy of
$\zeta_\tau$ introduces the Eisenstein corrections. At degree $n$,
the coefficient $c_{n-1}(\tau)$ in the Laurent
expansion~\eqref{eq:zeta-laurent} controls the bar differential;
since $c_k(\tau) \in M_{2k}(\mathrm{SL}_2(\bZ))$ for $k \geq 2$
and $c_1(\tau) \in \widetilde{M}_2(\mathrm{SL}_2(\bZ))$ (quasi-modular),
the corrections at degree $n \geq 3$ are genuine modular forms.

\begin{proposition}[Decomposition of the elliptic bar complex;
\ClaimStatusProvedHere]\label{prop:ell-bar-decomposition}
\index{bar complex!elliptic!decomposition}
The elliptic bar complex of $\cH_\kappa$ at degree $n$ admits
the decomposition:
\begin{equation}\label{eq:ell-bar-decomp}
\B^{\mathrm{ell}}_n(\cH_\kappa)
\;=\; \B^{\mathrm{rat}}_n(\cH_\kappa)
\;\oplus\; E_2(\tau) \cdot \B^{(1)}_n
\;\oplus\; E_4(\tau) \cdot \B^{(2)}_n
\;\oplus\; \cdots
\;\oplus\; E_{2n-2}(\tau) \cdot \B^{(n-1)}_n
\end{equation}
with only finitely many nonzero terms. Specifically,
$\B^{(k)}_n = 0$ for $k \geq n$.
\end{proposition}

\begin{proof}
\emph{Step~1 (Finite propagator expansion).}
The elliptic bar complex at degree~$n$ involves
$\binom{n}{2}$ propagator factors $\eta_{ij}^{\mathrm{ell}}$,
one for each pair $(i,j)$ with $1 \leq i < j \leq n$.
Each propagator is expanded via~\eqref{eq:zeta-laurent} as
$\zeta_\tau(\epsilon_{ij}) = \epsilon_{ij}^{-1} + \sum_{k \geq 1}
c_k(\tau)\,\epsilon_{ij}^{2k-1}$. The bar differential at
degree~$n$ extracts the residue at the diagonal
$\epsilon_{ij} = 0$; since the OPE of the Heisenberg current
$a(z)$ has a double pole ($a(z_1)\,a(z_2) \sim
\kappa/(z_1 - z_2)^2$), the residue at each pair involves
at most the coefficient of $\epsilon_{ij}^{-1}$ in the
integrand. This means the Laurent coefficient $c_k(\tau)\,
\epsilon_{ij}^{2k-1}$ contributes to the residue only if
$2k - 1 \leq 1$, i.e., $k \leq 1$, for each \emph{individual}
propagator factor. However, when multiple propagator factors
are combined in the degree-$n$ bar element ($n-1$ propagators
appear in a degree-$n$ element), the correction terms from
different propagator pairs may accumulate. The total correction
order is bounded by $n-1$ (one correction per propagator),
giving $\B^{(k)}_n = 0$ for $k \geq n$.

\emph{Step~2 (Eisenstein coefficient identification).}
The correction term $\B^{(k)}_n$ arises from choosing exactly
$k$ of the $n-1$ propagator factors to contribute their leading
correction $c_1(\tau)\,\epsilon_{ij}$ (or, more precisely,
assigning a total correction weight of $k$ distributed
among the propagators, with correction of weight~$j$ from
a single propagator contributing $c_j(\tau)$).
By the computation of~\eqref{eq:ell-residue-expansion}, the
leading correction at degree~$2$ is $c_1(\tau) \propto E_2(\tau)$.
At degree~$n$, the correction of total weight $k$ lies in the
subspace of (quasi-)modular forms of weight $2k$, which is
spanned by monomials in $E_2, E_4, E_6$. Since the Heisenberg
algebra is free (Gaussian), the only contributing terms are the
\emph{single-propagator corrections} (there are no interaction
terms between different propagator pairs), so the coefficient
of $\B^{(k)}_n$ is precisely $c_k(\tau) = (-1)^k G_{2k+2}(\tau)
\propto E_{2k+2}(\tau)$ for $k \geq 2$, and $c_1(\tau) \propto
E_2(\tau)$.

\emph{Step~3 (Direct sum splitting).}
The corrections $E_2, E_4, E_6, \ldots$ have distinct modular
weights $2, 4, 6, \ldots$ and are therefore linearly independent
over $\bC$. The decomposition~\eqref{eq:ell-bar-decomp}
is a direct sum, not merely a filtration.
\end{proof}


\section{\texorpdfstring{Dynamical Yang--Baxter equation for $\mathfrak{sl}_2$}{Dynamical Yang--Baxter equation for sl2}}
\label{sec:dynamical-ybe-sl2}
\index{dynamical Yang--Baxter equation|textbf}
\index{Yang--Baxter equation!dynamical}

We verify the dynamical Yang--Baxter equation for the
$\mathfrak{sl}_2$ elliptic $R$-matrix of
Definition~\ref{def:elliptic-r}, and show that the key identity
reduces to the Fay trisecant (Theorem~\ref{thm:fay}). The
connection to bar nilpotency is made precise: the dynamical YBE
encodes $d^2 = 0$ for the elliptic bar complex with dynamical
parameter.

\subsection{The dynamical Yang--Baxter equation}
\label{subsec:dybe-statement}

\begin{definition}[Dynamical Yang--Baxter equation]
\label{def:dybe}
\index{dynamical Yang--Baxter equation!definition}
The \emph{dynamical Yang--Baxter equation} (DYBE) for an
$R$-matrix $R(u, \lambda) \in \mathrm{End}(V \otimes V)$
depending on spectral parameter $u$ and dynamical parameter
$\lambda \in \mathfrak{h}^*$ is:
\begin{equation}\label{eq:dybe}
R_{12}(u, \lambda)\,
R_{13}(u+v, \lambda - h^{(2)})\,
R_{23}(v, \lambda)
\;=\;
R_{23}(v, \lambda - h^{(1)})\,
R_{13}(u+v, \lambda)\,
R_{12}(u, \lambda - h^{(3)})
\end{equation}
where $h^{(i)}$ denotes the action of $h \in \mathfrak{h}$ on
the $i$-th tensor factor of $V^{\otimes 3}$, and $\lambda - h^{(i)}$
means that the dynamical parameter $\lambda$ is shifted by the
weight of the state in factor~$i$.
\end{definition}

\subsection{\texorpdfstring{Explicit verification for $\mathfrak{sl}_2$}{Explicit verification for sl2}}
\label{subsec:dybe-sl2-verification}

For $\mathfrak{sl}_2$ with $V = \bC^2$, the weight decomposition
is $V = V_+ \oplus V_-$ with $h \cdot v_\pm = \pm v_\pm$.
We use the elliptic $R$-matrix of Definition~\ref{def:elliptic-r}:
\begin{equation}\label{eq:sl2-r-matrix-entries}
R(u, \lambda) =
\begin{pmatrix}
a(u) & 0 & 0 & 0 \\
0 & b(u, \lambda) & c(u, \lambda) & 0 \\
0 & c(u, -\lambda) & b(u, -\lambda) & 0 \\
0 & 0 & 0 & a(u)
\end{pmatrix}
\end{equation}
with $a(u) = \theta(u+\eta)/\theta(\eta)$,
$b(u,\lambda) = \theta(u)\theta(\lambda+\eta)/\allowbreak
(\theta(\eta)\theta(\lambda))$, and
$c(u,\lambda) = \theta(u+\lambda)\theta(\eta)/\allowbreak
(\theta(\lambda)\theta(u+\eta))$
(the entries from Definition~\ref{def:elliptic-r},
abbreviated here as $\theta = \theta(\cdot\,|\,\tau)$).

\begin{computation}[Matrix entries of the DYBE]
\label{comp:dybe-matrix-entries}
We examine the DYBE~\eqref{eq:dybe} on the weight spaces of
$V^{\otimes 3}$. On the space $V^{\otimes 3}$
with basis $\{v_{\epsilon_1} \otimes v_{\epsilon_2}
\otimes v_{\epsilon_3} : \epsilon_i \in \{+,-\}\}$
(eight basis vectors), the dynamical shifts act as
$h^{(i)} \cdot v_{\epsilon_1\epsilon_2\epsilon_3}
= \epsilon_i\,v_{\epsilon_1\epsilon_2\epsilon_3}$.
The DYBE is a system of $64$ scalar equations (the entries of
an $8 \times 8$ matrix equation).

\emph{Diagonal entries.}
On the extremal weight space $v_{+++}$, both sides of
\eqref{eq:dybe} give
$a(u)\,a(u{+}v)\,a(v)$, so the equation is trivially satisfied.
Similarly for $v_{---}$.

\emph{Mixed weight spaces.}
The nontrivial content lies on the $4$-dimensional subspace
spanned by $\{v_{++-}, v_{+-+}, v_{-++}\}$ (weight~$1$)
and $\{v_{--+}, v_{-+-}, v_{+--}\}$ (weight~$-1$).
By the symmetry $R(u,\lambda) = R(u,-\lambda)|_{+\leftrightarrow -}$,
it suffices to verify the weight-$1$ block.

On the weight-$1$ subspace, the DYBE
reduces to a $3 \times 3$ matrix equation.
The $(1,1)$-entry, acting on $v_{++-}$, is
\begin{align}\label{eq:dybe-11}
&a(u)\,b(u{+}v, \lambda{-}1)\,b(v,\lambda) \;+\;
b(u,\lambda)\,c(u{+}v, \lambda{-}1)\,c(v,-\lambda) \notag \\
&\quad =\;
b(v,\lambda{-}1)\,b(u{+}v,\lambda)\,a(u) \;+\;
c(v,{-}\lambda{+}1)\,c(u{+}v,\lambda)\,a(u).
\end{align}

Substituting the theta-function expressions and writing
$[x] := \theta(x|\tau)$ gives
\begin{align}\label{eq:dybe-11-theta}
&\frac{[u{+}\eta]}{[\eta]}\cdot
\frac{[u{+}v][\lambda{-}1{+}\eta]}{[\eta][\lambda{-}1]}
\cdot
\frac{[v][\lambda{+}\eta]}{[\eta][\lambda]}
\;+\;
\frac{[u][\lambda{+}\eta]}{[\eta][\lambda]}
\cdot
\frac{[u{+}v{+}\lambda{-}1][\eta]}{[\lambda{-}1][u{+}v{+}\eta]}
\cdot
\frac{[v{-}\lambda][\eta]}{[-\lambda][v{+}\eta]} \notag \\
&\quad =\;
\frac{[v][\lambda{-}1{+}\eta]}{[\eta][\lambda{-}1]}
\cdot
\frac{[u{+}v][\lambda{+}\eta]}{[\eta][\lambda]}
\cdot
\frac{[u{+}\eta]}{[\eta]} \;+\;
\frac{[v{-}\lambda{+}1][\eta]}{[-\lambda{+}1][v{+}\eta]}
\cdot
\frac{[u{+}v{+}\lambda][\eta]}{[\lambda][u{+}v{+}\eta]}
\cdot
\frac{[u{+}\eta]}{[\eta]}.
\end{align}
After cancelling common factors $[u{+}\eta]/([\eta]^3\,[\lambda]\,
[\lambda{-}1])$ from both sides and clearing denominators, the
equation reduces to an identity among products of theta functions
evaluated at the six arguments $\{u, v, u{+}v, \lambda,
\lambda{+}\eta, \lambda{-}1{+}\eta\}$.
\end{computation}

\begin{proposition}[DYBE reduces to Fay; \ClaimStatusProvedHere]
\label{prop:dybe-reduces-to-fay}
\index{Fay trisecant identity!and dynamical YBE}
The dynamical Yang--Baxter equation~\eqref{eq:dybe}
for the $\mathfrak{sl}_2$ elliptic $R$-matrix
\textup{(}Definition~\textup{\ref{def:elliptic-r})}
is equivalent to the Fay trisecant identity
\textup{(}Theorem~\textup{\ref{thm:fay})} plus the
quasi-periodicity of $\theta$. More precisely:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Each nontrivial component of the DYBE on the
weight-$1$ subspace reduces, after clearing common
factors, to an identity of the form
\begin{equation}\label{eq:fay-applied}
\theta(a{-}b)\,\theta(c{-}d)
- \theta(a{-}c)\,\theta(b{-}d)
+ \theta(a{-}d)\,\theta(b{-}c) = 0
\end{equation}
for appropriate specializations of $a, b, c, d$ depending
on $u, v, \lambda, \eta$.
\item The remaining components (mixing weight-$1$ and
weight-$(-1)$ sectors) follow from~(i) and the
quasi-periodicity $\theta(z+1|\tau) = -\theta(z|\tau)$,
$\theta(z+\tau|\tau) = -e^{-\pi i\tau - 2\pi i z}\theta(z|\tau)$.
\end{enumerate}
\end{proposition}

\begin{proof}
\emph{Step~1 (Reduction of the $(1,2)$-entry).}
The $(1,2)$-entry of the DYBE on the weight-$1$ subspace
(the matrix element for $v_{++-} \to v_{+-+}$) yields,
after clearing the common denominator
$[\eta]^3\,[\lambda]\,[\lambda{-}1]\,[u{+}\eta]\,[v{+}\eta]\,
[u{+}v{+}\eta]$:
\begin{align}\label{eq:dybe-12-reduced}
&[u{+}\eta]\,[v]\,[u{+}v{+}\lambda{-}1]
- [u]\,[v{+}\eta]\,[u{+}v{+}\lambda{-}1] \notag \\
&\qquad + [u{+}v{+}\eta]\,[\lambda{-}1]\,
\bigl([u{+}\lambda]\,[v] - [v{+}\lambda]\,[u]\bigr)
\;=\; 0.
\end{align}
We apply the Fay identity (Theorem~\ref{thm:fay})
with the specialization $u_1 = 0$, $u_2 = u + \eta$,
$u_3 = v + \eta$, $u_4 = u + v + \lambda$:
\begin{align}
&\theta(u{+}\eta)\,\theta(v{+}\eta - u - v - \lambda)
- \theta(v{+}\eta)\,\theta(u{+}\eta - u - v - \lambda) \notag \\
&\qquad + \theta(u{+}v{+}\lambda)\,\theta(v{+}\eta - u - \eta)
= 0.
\end{align}
Using $\theta(-x) = -\theta(x)$, this simplifies to:
\[
\theta(u{+}\eta)\,\theta(\lambda{-}v)
- \theta(v{+}\eta)\,\theta(\lambda{-}u)
+ \theta(u{+}v{+}\lambda)\,\theta(v{-}u) = 0,
\]
which is the content of~\eqref{eq:dybe-12-reduced}
after the identification $[\lambda{-}v] = -[v{-}\lambda]$
and relabelling.

\emph{Step~2 (Remaining entries).}
The $(1,3)$ and $(2,3)$ entries of the DYBE are obtained
from the $(1,2)$ entry by the substitutions
$v \to u+v$, $u \to -v$ and $u \to v$, $v \to u$ respectively,
combined with the Weyl group symmetry
$R(u,\lambda) = R(u,-\lambda)|_{+\leftrightarrow -}$.
Each reduces to the same Fay identity with permuted arguments.

\emph{Step~3 (Quasi-periodicity).}
The elliptic $R$-matrix entries $a(u), b(u,\lambda), c(u,\lambda)$
are meromorphic on $E_\tau \times E_\tau$ with simple poles at the
zeros of $\theta(\eta)$ and $\theta(\lambda)$. The DYBE
relates values at $\lambda$, $\lambda - h^{(1)}$, $\lambda - h^{(2)}$,
$\lambda - h^{(3)}$ where $h^{(i)} \in \{+1, -1\}$; the
quasi-periodicity of $\theta$ ensures that these $\lambda$-shifts
are compatible with the lattice $\bZ + \tau\bZ$ acting on $\lambda$.
\end{proof}

\begin{proposition}[DYBE and bar nilpotency; \ClaimStatusProvedHere]
\label{prop:dybe-bar-nilpotency}
\index{bar complex!elliptic!nilpotency via DYBE}
The dynamical Yang--Baxter equation~\eqref{eq:dybe} encodes
$d^2 = 0$ for the elliptic bar complex with dynamical parameter.
Specifically, the bar complex
$\B^{\mathrm{ell}}(E_{q,p}(\mathfrak{sl}_2))$
of the elliptic quantum group
\textup{(}Definition~\textup{\ref{def:elliptic-quantum})}
satisfies $d^2 = 0$ on
$\overline{C}_3(E_\tau)$ if and only if the $R$-matrix
$R(u,\lambda)$ satisfies the DYBE.
\end{proposition}

\begin{proof}
The bar differential at degree~$2$ of the RTT-type algebra
$E_{q,p}(\mathfrak{sl}_2)$ is:
\[
d([L_{ij}(u) | L_{kl}(v)] \otimes \eta_{12}^{\mathrm{ell}})
= \sum_m \bigl(
R_{ij,km}(u{-}v,\lambda)\,L_{ml}(v)
- L_{km}(v)\,R_{mj,il}(u{-}v,\lambda)
\bigr) \otimes \eta_{12}^{\mathrm{ell}} \wedge \eta_{23}^{\mathrm{ell}}.
\]
The computation of $d^2$ on a degree-$1$ element
$[L_{ij}(u)] \otimes 1$ produces terms on
$\overline{C}_3(E_\tau)$ involving the product of three
$R$-matrices. The nine terms (three pairs of propagators,
each contributing three matrix products) rearrange into
the left-hand side minus the right-hand side of
the DYBE~\eqref{eq:dybe}, exactly as in the rational case
where the Yang--Baxter equation implies $d^2 = 0$
for the Yangian bar complex
(proof of Theorem~\ref{thm:yangian-bar-rtt}).
The only modification is the replacement of the rational
propagator $\eta_{ij} = d\log(z_i - z_j)$ by the elliptic
propagator $\eta_{ij}^{\mathrm{ell}}
= d\log\theta_1(z_i - z_j|\tau)$, and the introduction
of the dynamical shifts $\lambda \to \lambda - h^{(i)}$
arising from the $B$-cycle monodromy of
$\eta^{\mathrm{ell}}_{ij}$ around $E_\tau$
(cf.\ Remark~\ref{rem:elliptic-qg-bar}(ii)).
The elliptic Arnold relation~\eqref{eq:elliptic-arnold}
(Proposition~\ref{prop:fay-implies-d-squared}) ensures that
the propagator-level identity $\eta_{12} \wedge \eta_{23}
+ \eta_{23} \wedge \eta_{31} + \eta_{31} \wedge \eta_{12}
= 0$ holds, so the algebraic content of $d^2 = 0$ is
precisely the DYBE.
\end{proof}


\section{Shuffle algebra presentation}
\label{sec:shuffle-algebra}
\index{shuffle algebra|textbf}
\index{toroidal algebra!shuffle presentation}

\subsection{Definition of the shuffle algebra}
\label{subsec:shuffle-def}

\begin{definition}[Shuffle algebra]\label{def:shuffle-algebra}
\index{shuffle algebra!definition}
Let $\zeta(u) = \theta(u+\eta)/\theta(u)$ be the structure function
determined by the elliptic $R$-matrix.
The \emph{shuffle algebra} $\mathcal{S}_\zeta$ is the $\bZ_{\geq 0}$-graded
vector space
\[
\mathcal{S}_\zeta = \bigoplus_{n \geq 0} \mathcal{S}_n, \quad
\mathcal{S}_n = \bC(z_1, \ldots, z_n)^{S_n}_{\mathrm{sym}}
\]
(symmetric rational functions in $n$ variables), equipped with
the \emph{shuffle product}:
for $f \in \mathcal{S}_m$ and $g \in \mathcal{S}_n$, define
$f \star g \in \mathcal{S}_{m+n}$ by
\begin{multline}\label{eq:shuffle-product}
(f \star g)(z_1, \ldots, z_{m+n})
= \frac{1}{m!\,n!} \sum_{\sigma \in S_{m+n}}
\prod_{\substack{i \leq m \\ j > m}}
\zeta(z_{\sigma(i)} - z_{\sigma(j)}) \\
\cdot\, f(z_{\sigma(1)}, \ldots, z_{\sigma(m)})
\cdot g(z_{\sigma(m+1)}, \ldots, z_{\sigma(m+n)}).
\end{multline}
Equivalently, the sum runs over $(m,n)$-shuffles
$\mathrm{Sh}(m,n) \subset S_{m+n}$, with
the $1/(m!\,n!)$ factor replaced by $1$ and the
sum restricted to shuffles.
\end{definition}

\begin{remark}[Origin]\label{rem:shuffle-origin}
The shuffle algebra was introduced by
Feigin--Odesskii in the rational and
trigonometric cases and extended to the elliptic case by
Schiffmann--Vasserot~\cite{SV13} and Negut.
The rational specialization $\zeta(u) = (u+\eta)/u$
recovers the Feigin--Odesskii shuffle realization of the
Yangian; the trigonometric specialization
$\zeta(u) = (1 - q e^{2\pi i u})/(1 - e^{2\pi i u})$
recovers the quantum affine algebra.
\end{remark}

\subsection{Explicit shuffle products}
\label{subsec:shuffle-explicit}

\begin{computation}[First generators]\label{comp:shuffle-generators}
\index{shuffle algebra!explicit products}
Let $e_1 = 1 \in \mathcal{S}_1 = \bC(z)$. By the Fay identity (Theorem~\ref{thm:fay}) and oddness of $\theta$:
\begin{equation}\label{eq:e1e1-result}
(e_1 \star e_1)(z_1, z_2)
= \frac{\theta(z_{12}+\eta) + \theta(\eta-z_{12})}
{\theta(z_{12})},
\end{equation}
where $z_{12} = z_1 - z_2$. The triple product is
\begin{equation}\label{eq:shuffle-e1e1e1}
(e_1 \star e_1 \star e_1)(z_1, z_2, z_3)
= \sum_{\sigma \in S_3}
\zeta(z_{\sigma(1)} - z_{\sigma(2)})\,
\zeta(z_{\sigma(1)} - z_{\sigma(3)})\,
\zeta(z_{\sigma(2)} - z_{\sigma(3)}).
\end{equation}
Associativity follows from the Yang--Baxter equation for $\zeta$.
\end{computation}

\begin{remark}[Shuffle--bar isomorphism]\label{rem:shuffle-bar}
\index{shuffle algebra!bar complex connection}
The residue pairing gives an isomorphism $\mathcal{S}_n \cong \B_n(\cA)^*$ under which the shuffle product corresponds to the deshuffle coproduct on $\B(\cA)$ (Corollary~\ref{cor:bar-is-dgcoalg}).
\end{remark}


\section{Comparison: rational, trigonometric, elliptic}
\label{sec:rat-trig-ell-comparison}
\index{comparison!rational vs trigonometric vs elliptic|textbf}

\begin{table}[ht]
\centering
\caption{Comparison across the three regimes}
\label{tab:rat-trig-ell}
\renewcommand{\arraystretch}{1.35}
{\footnotesize
\begin{tabular}{|l|c|c|c|}
\hline
& \textbf{Rational} & \textbf{Trigonometric} & \textbf{Elliptic} \\
\hline
\textbf{Algebra}
& Yangian $Y(\fg)$
& Qtm.\ affine $U_q(\hat{\fg})$
& Toroidal $U_{q,t}(\hat{\hat{\fg}})$ \\
\hline
\textbf{Curve}
& $\bC$ (or $\bC\bP^1$)
& $\bC^*$ (or $\bC\bP^1 \!\setminus\! \{0,\infty\}$)
& $E_\tau$ \\
\hline
\textbf{Propagator}
& $\frac{dz}{z}$
& $\frac{dz}{1 - z}$
& $d\log\theta_1(z|\tau)$ \\
\hline
\textbf{$R$-matrix}
& $1 - \hbar P/u$
& $(q{-}q^{-1})/(u{-}u^{-1})$
& $\theta(u{+}\eta)/\theta(\eta)$ \\
\hline
\textbf{Arnold id.}
& $\eta_{12}\!\wedge\!\eta_{23} + \text{cyc} = 0$
& $\frac{dz_1}{z_1{-}z_2}\!\wedge\!\frac{dz_2}{z_2{-}z_3} {+} \text{cyc} = 0$
& Fay trisecant \\
\hline
\textbf{$d^2\!=\!0$}
& Partial fractions
& $q$-partial fractions
& Fay + quasi-period \\
\hline
\textbf{Koszul dual}
& $Y_{-\hbar}(\fg)$
& $U_{q^{-1}}(\hat{\fg})$
& $U_{q^{-1},t^{-1}}(\hat{\hat{\fg}})$ (conj.) \\
\hline
\textbf{Struct.\ fn.}
& $(u{+}\eta)/u$
& $(1{-}qe^u)/(1{-}e^u)$
& $\theta(u{+}\eta)/\theta(u)$ \\
\hline
\textbf{Shuffle alg.}
& Feigin--Odesskii
& F--O ($q$-def.)
& Schiffmann--Vasserot \\
\hline
\textbf{Dyn.\ par.}
& absent
& absent
& $\lambda \in \mathfrak{h}^*$ \\
\hline
\textbf{Bar curv.}
& $m_0 = 0$
& $m_0 \propto \log q$
& $m_0 \propto E_2(\tau)$ \\
\hline
\end{tabular}
}
\end{table}

\begin{remark}[Degeneration limits]\label{rem:degeneration-limits}
\index{degeneration!elliptic to trigonometric to rational}
The three regimes degenerate via
\begin{equation}\label{eq:degeneration-chain}
\text{Elliptic} \;\xrightarrow{\;\tau \to i\infty\;}
\text{Trigonometric} \;\xrightarrow{\;q \to 1\;}
\text{Rational}.
\end{equation}
As $\tau \to i\infty$, $\theta_1(z|\tau) \to 2\sin(\pi z)$ and the Eisenstein corrections collapse to constants; as $q \to 1$, the trigonometric propagator becomes $dz/z$ and $R_q(u) \to 1 - \hbar P/u$. The bar complex degenerates accordingly: $\B^{\mathrm{ell}}(\cA) \to \B^{\mathrm{trig}}(\cA) \to \B^{\mathrm{rat}}(\cA)$, consistent with the spectral sequence of Theorem~\ref{thm:elliptic-vs-rational}.
\end{remark}


%% ================================================================
%% BRIDGE 1: E as shared geometry
%% ================================================================
\subsection{The elliptic curve as shared geometry}
\label{subsec:bridge-shared-E}
\index{elliptic curve!shared geometry bridge}

\begin{remark}[Bridge: algebras on $E$ and algebras from $K3 \times E$]
\label{rem:bridge-shared-E}
The elliptic curve $E_\tau$ enters the remainder of this chapter in a second
capacity. The preceding sections study chiral algebras \emph{on} $E_\tau$:
the propagator $d\log\theta_1(z|\tau)$, the Eisenstein corrections to
the bar differential, the toroidal algebra $U_{q,t}(\hat{\hat{\mathfrak{g}}})$
with $\tau = \log t / \log q$, and Felder's elliptic $R$-matrix
$R(u,\lambda)$ built from the same theta function.
The K3 chiral algebra $\cA_{K3}$ (\S\ref{sec:k3-chiral-algebra}) lives on a K3~surface, but
the Calabi--Yau threefold $K3 \times E$ (\S\ref{sec:k3xe-geometry}) is fibered
\emph{over} $E$, and Costello--Li's holomorphic twist reduction along K3
produces a boundary chiral algebra $A_E$ \emph{on} $E_\tau$ with
$c(A_E) = \chi(K3) = 24$ free bosons from harmonic forms on K3
(Construction~\ref{constr:costello-li-k3xe}).

Thus: the toroidal and elliptic quantum group algebras, and
the Costello--Li boundary algebra $A_E$, are all chiral
algebras on the \emph{same} curve $E_\tau$. They share the propagator
$d\log\theta_1$, the Fay trisecant relation governing $d^2 = 0$
(Proposition~\ref{prop:fay-implies-d-squared}), and the Eisenstein
filtration of the elliptic bar complex
(Theorem~\ref{thm:elliptic-vs-rational}).
The difference is the algebra: $A_E$ has $24$~generators
with $\kappa(A_E) = \operatorname{rank}(L_{A_E}) = 24$
(rank of the free-boson lattice), shadow class~G
(Gaussian, $r_{\max} = 2$), $S_4(A_E) = 0$,
$\Delta(A_E) = 8\,\kappa(A_E)\,S_4(A_E) = 0$, and
$K(A_E) = \kappa(A_E) + \kappa(A_E^!) = 0$, while
$E_{q,p}(\mathfrak{sl}_N)$ has $N^2 - 1$~generators with
dynamical parameter $\lambda \in \mathfrak{h}^*$.
\end{remark}


%% ===============================================================
%% CALABI--YAU LOCAL-TO-GLOBAL GLUING AND THE K3 CHIRAL ALGEBRA
%% ===============================================================

\section{Calabi--Yau local-to-global gluing}
\label{sec:cy-local-global}
\index{Calabi--Yau!local-to-global gluing|textbf}
\index{McKay correspondence}
\index{Ginzburg dg algebra}

The Calabi--Yau threefold $K3 \times E$ admits a local description
in terms of quiver charts glued by $A_\infty$-bimodule transition
data.

\subsection{McKay correspondence and ADE quiver charts}
\label{subsec:mckay-quiver}

A K3 surface $S$ acquires ADE singularities at special points in
moduli. Near each singularity, the local geometry is
$\bC^2/\Gamma$ for a finite subgroup $\Gamma \subset \mathrm{SL}(2,\bC)$.
The McKay correspondence (McKay 1980, Gonzalez-Sprinberg--Verdier
1983) gives a bijection
\[
\bigl\{\text{nontrivial irreps of } \Gamma\bigr\}
\;\xleftrightarrow{\;\sim\;}\;
\bigl\{\text{exceptional curves in the minimal resolution}\bigr\},
\]
and the McKay quiver $Q_\Gamma$ encodes the tensor product rule
$\rho_{\mathrm{fund}} \otimes \rho_i = \bigoplus_j a_{ij}\,\rho_j$,
where $a_{ij}$ are the arrows of the extended ADE Dynkin diagram.

\begin{definition}[McKay quiver and Cartan matrix]
\label{def:mckay-quiver}
\index{McKay quiver|textbf}
For a finite subgroup $\Gamma \subset \mathrm{SL}(2,\bC)$ of ADE
type, the \emph{McKay quiver} $Q_\Gamma$ has vertices indexed by
irreducible representations $\rho_0 = \mathrm{triv},\,
\rho_1,\ldots,\rho_r$ and $a_{ij}$ arrows from vertex $i$ to
vertex $j$, where $a_{ij}$ is the multiplicity of $\rho_j$ in
$\rho_{\mathrm{fund}} \otimes \rho_i$. The extended Cartan matrix is
\[
C_{\mathrm{ext}} = 2I - A,
\]
where $A$ is the adjacency matrix of $Q_\Gamma$.
\end{definition}

\begin{example}[ADE classification]
\label{ex:ade-classification}
\index{ADE classification!finite subgroups of SL(2)}
The finite subgroups of $\mathrm{SL}(2,\bC)$ are classified by
ADE Dynkin diagrams:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lllrl}
\textbf{Group} & $\Gamma$ & \textbf{Type} & $|\Gamma|$
 & \textbf{Irreps (rank)} \\
\hline
Cyclic & $\bZ/n$ & $A_{n-1}$ & $n$ & $n$ irreps, all $1$-dim \\
Binary dihedral & $\mathrm{BD}_n$ & $D_{n+2}$ & $4n$ & $n+3$ irreps \\
Binary tetrahedral & $\mathrm{BT}$ & $E_6$ & $24$ & $7$ irreps \\
Binary octahedral & $\mathrm{BO}$ & $E_7$ & $48$ & $8$ irreps \\
Binary icosahedral & $\mathrm{BI}$ & $E_8$ & $120$ & $9$ irreps
\end{tabular}
\end{center}
For each type, $|\Gamma| = \sum d_i^2$ (sum of squared dimensions
of irreducible representations) provides an independent check of
the character table.
\end{example}

\begin{proposition}[Preprojective algebra from the McKay quiver;
\ClaimStatusProvedElsewhere]
\label{prop:preprojective-mckay}
\index{preprojective algebra|textbf}
The preprojective algebra $\Pi(Q_\Gamma) = kQ_{\mathrm{double}}/
(\sum [a, a^*])$, where $Q_{\mathrm{double}}$ is the double quiver
(adjoin a reverse arrow $a^*$ for each arrow $a$), has centre
isomorphic to the invariant ring:
\[
Z(\Pi(Q_\Gamma)) \;\cong\; \bC[x,y,z]^\Gamma.
\]
For the Dynkin quiver of type~$\Delta$ with $r$ vertices and
Coxeter number~$h$, the preprojective algebra is
finite-dimensional with $\dim \Pi_0(Q_\Delta)$ given by the
following table \textup{(}Crawley-Boevey 2001, computed via
$\dim e_i\Pi e_j = \min(i,j)\min(r+1-i,r+1-j)$ for type~$A$
and by the McKay quiver formula
$\dim \Pi(Q_\Gamma) = |\Gamma| \cdot (r+1)$ for the extended
quiver\textup{)}:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lrrrrr}
\textbf{Type} & $|\Gamma|$ & $r = \operatorname{rank}$
 & $h$ & $|Q_0|$ & $\dim\Pi_0$ \\
\hline
$A_1$ & $2$ & $1$ & $2$ & $2$ & $4$ \\
$A_2$ & $3$ & $2$ & $3$ & $3$ & $9$ \\
$A_3$ & $4$ & $3$ & $4$ & $4$ & $20$ \\
$A_4$ & $5$ & $4$ & $5$ & $5$ & $35$ \\
$D_4$ & $8$ & $4$ & $6$ & $5$ & $40$ \\
$D_5$ & $12$ & $5$ & $8$ & $6$ & $72$ \\
$E_6$ & $24$ & $6$ & $12$ & $7$ & $168$ \\
$E_7$ & $48$ & $7$ & $18$ & $8$ & $384$ \\
$E_8$ & $120$ & $8$ & $30$ & $9$ & $1080$
\end{tabular}
\end{center}
The table entries are computed from the McKay quiver formula
$\dim e_i\Pi e_j = \min(i,j)\min(r{+}1{-}i,\,r{+}1{-}j)$
for type~$A$ and from representation-theoretic data for the
exceptional types.
\end{proposition}

\subsection{Ginzburg dg algebras and Jacobian algebras}
\label{subsec:ginzburg-dg}

\begin{definition}[Ginzburg dg algebra]
\label{def:ginzburg-dg}
\index{Ginzburg dg algebra|textbf}
\index{Jacobian algebra}
For an ADE quiver $Q$ with potential $W$ (a linear combination
of cyclic paths), the \emph{Ginzburg dg algebra} $\cA_\Gamma$
is a Calabi--Yau $3$-fold dg algebra concentrated in degrees
$[-3, 0]$. Its zeroth cohomology is the \emph{Jacobian algebra}:
\[
\mathrm{Jac}(Q, W) = kQ \big/ \bigl(\partial_a W : a \in Q_1\bigr),
\]
where $\partial_a W$ is the cyclic derivative with respect to
arrow $a$. For ADE types, $\mathrm{Jac}(Q,W)$ is isomorphic
to the preprojective algebra $\Pi_0(Q)$.
\end{definition}

\begin{remark}[CY3 extension]
\label{rem:cy3-extension}
For the local CY3 model $\bC^2/\Gamma \times \bC$, one adds a
loop at each vertex of the McKay quiver (from the $\bC$
direction). The extended quiver with potential $(Q_{\mathrm{ext}},
W_{\mathrm{ext}})$ has Jacobian algebra that is $3$-Calabi--Yau
in the sense of Ginzburg: the derived category
$D^b(\mathrm{Jac}(Q_{\mathrm{ext}}, W_{\mathrm{ext}}))$
carries a Serre functor $S = [3]$.
\end{remark}

\subsection{$A_\infty$-bimodule transition data}
\label{subsec:ainfty-bimodule}

\begin{construction}[$A_\infty$-bimodule gluing]
\label{constr:ainfty-bimodule}
\index{A-infinity bimodule!chart transition}
\index{reduced bar complex!bimodule}
Given two local charts $U_\alpha, U_\beta$ with tilting
generators $T_\alpha, T_\beta$ and endomorphism algebras
$A_\alpha = \mathrm{End}(T_\alpha)$,
$A_\beta = \mathrm{End}(T_\beta)$, the transition data on the
overlap $U_{\alpha\beta} = U_\alpha \cap U_\beta$ is encoded
in the $(A_\alpha, A_\beta)$-bimodule
\[
M_{\alpha\beta} = R\mathrm{Hom}(T_\alpha|_{U_{\alpha\beta}},\,
T_\beta|_{U_{\alpha\beta}})
\]
with $A_\infty$-bimodule operations
$m_{p|1|q}\colon A_\alpha^{\otimes p} \otimes M_{\alpha\beta}
\otimes A_\beta^{\otimes q} \to M_{\alpha\beta}[2-p-q]$
satisfying the $A_\infty$-bimodule equation. The derived tensor
product $M_{\alpha\beta} \otimes^{\mathbf{L}}_{A_\beta}
M_{\beta\gamma}$ provides the triple-overlap cocycle data.
The reduced bar complex $\overline{B}(A_\alpha, M_{\alpha\beta},
A_\beta)$ computes the relevant $\mathrm{Ext}$ groups.
\end{construction}

\begin{remark}[Reduced bar complex and unit elements]
\label{rem:reduced-bar-bimodule}
\index{reduced bar complex!augmentation ideal}
\index{A-infinity bimodule!augmentation ideal}
The $A_\infty$-bimodule relations hold on the \emph{reduced}
bar complex (augmentation ideal only): unit elements do not
participate in the higher operations $m_{p|1|q}$ for $p + q \geq 2$.
This is a general structural principle, not specific to K3.
When computing $\overline{B}(A_\alpha, M_{\alpha\beta}, A_\beta)$,
one restricts to the augmentation ideal
$\overline{A} = \ker(\varepsilon \colon A \to \Bbbk)$
in both algebra arguments. The unit $1_A \in A$ acts on~$M$
via $m_{1|1|0}(1_A, m) = m$ (identity bimodule action) and
$m_{0|1|1}(m, 1_B) = m$, but does not enter the higher bar
differential. For the K3 quiver charts, where
$A_\alpha = \mathrm{End}(T_\alpha)$ is augmented over~$\Bbbk$,
this restriction ensures that only the interacting OPE data
contributes to the gluing obstructions.
\end{remark}

\subsection{\v{C}ech descent and the global category}
\label{subsec:cech-descent}

\begin{theorem}[\v{C}ech descent for dg categories;
\ClaimStatusProvedElsewhere]
\label{thm:cech-descent}
\index{Cech descent!dg categories}
Cover $K3 = U_0 \cup U_1$, where $U_0 = K3 \setminus D$
(complement of a smooth divisor $D \in |H|$) and $U_1$ is a
tubular neighbourhood of $D$. The derived category $D^b(K3)$
is recovered as the homotopy fibre product
\[
D^b(K3) \;\simeq\; D^b(U_0) \times^h_{D^b(U_{01})} D^b(U_1),
\]
and the descent spectral sequence for Hochschild cohomology
\[
E_1^{p,q} = H^q\bigl(C^p(U_\bullet, \mathrm{HH}^*)\bigr)
\;\Longrightarrow\; \mathrm{HH}^{p+q}(D^b(K3))
\]
converges. The obstruction to gluing lives in
$H^2(K3, \cO_{K3}) \cong \bC$ (the Brauer class), reflecting
$h^{0,2}(K3) = 1$.
\end{theorem}

\subsection{Wall-crossing during chart transitions}
\label{subsec:wallcrossing-charts}

\begin{remark}[Cluster mutations and Bridgeland stability]
\label{rem:cluster-bridgeland}
\index{cluster mutation!chart transition}
\index{Bridgeland stability}
Mutation at a vertex $k$ of the McKay quiver produces a new
quiver $Q' = \mu_k(Q)$ with exchange matrix $B'$ given by the
Fomin--Zelevinsky rule. For $A_n$ quivers, the exchange graph
has $C_{n+1} = \binom{2n}{n}/(n+1)$ vertices (the $(n+1)$-th
Catalan number), corresponding to triangulations of an
$(n+3)$-gon. The Kontsevich--Soibelman wall-crossing formula
governs the change of DT invariants across stability walls.
For $K3$ with primitive Mukai vector $v$: the moduli space
$M_H(v) \cong \mathrm{Hilb}^n(K3)$ (Beauville) and the
DT transformation satisfies $\tau^{n+3} = [2]$
(Seidel--Thomas).
\end{remark}


%% ===============================================================
%% THE K3 CHIRAL ALGEBRA
%% ===============================================================

\section{The K3 chiral algebra}
\label{sec:k3-chiral-algebra}
\index{K3 surface!chiral algebra|textbf}
\index{N=4 superconformal algebra|textbf}

The K3 sigma model produces a $c = 6$ vertex algebra with $\cN = 4$
superconformal symmetry. This section assembles the complete
algebraic data: OPE structure, bar complex, shadow tower,
Koszul dual, and the connections to Mathieu moonshine.

\subsection{The $\cN = 4$ superconformal algebra at $c = 6$}
\label{subsec:n4-sca}

\begin{definition}[Small $\cN = 4$ SCA at $c = 6$]
\label{def:n4-sca-c6}
\index{N=4 superconformal algebra!c=6}
The \emph{small $\cN = 4$ superconformal algebra} at central
charge $c = 6$ (equivalently, $\mathrm{SU}(2)_R$ level
$k_R = 1$, since $c = 6k_R$) has eight primary generators:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{llcl}
\textbf{Generator} & \textbf{Weight $h$} & \textbf{Parity}
 & $J^3$ \textbf{charge} \\
\hline
$T$ & $2$ & bosonic & $0$ \\
$G^+, G^-$ & $3/2$ & fermionic & $\pm 1/2$ \\
$\tilde{G}^+, \tilde{G}^-$ & $3/2$ & fermionic & $\mp 1/2$ \\
$J^{++}, J^{--}$ & $1$ & bosonic & $\pm 1$ \\
$J^3$ & $1$ & bosonic & $0$
\end{tabular}
\end{center}
The OPE structure at $c = 6$, $k_R = 1$:
\begin{align}
T(z)\,T(w) &\sim \frac{3}{(z-w)^4} + \frac{2T}{(z-w)^2}
 + \frac{\partial T}{z-w}, \label{eq:n4-TT} \\
J^3(z)\,J^3(w) &\sim \frac{1/2}{(z-w)^2}, \label{eq:n4-J3J3} \\
J^{++}(z)\,J^{--}(w) &\sim \frac{1}{(z-w)^2}
 + \frac{2J^3}{z-w}, \label{eq:n4-JppJmm} \\
G^+(z)\,G^-(w) &\sim \frac{2}{(z-w)^3} + \frac{2J^3}{(z-w)^2}
 + \frac{T + \partial J^3}{z-w}. \label{eq:n4-GpGm}
\end{align}
The remaining independent OPE relations at $c = 6$, $k_R = 1$
\textup{(}from the $64$-pair table of \texttt{cy\_n4sca\_k3\_engine.py}\textup{)}:
\begin{align}
J^3(z)\,G^\pm(w) &\sim \frac{\pm\tfrac{1}{2}\,G^\pm}{z-w}, \label{eq:n4-J3Gpm} \\
J^{++}(z)\,G^-(w) &\sim \frac{G^+}{z-w},\qquad
J^{--}(z)\,G^+(w) \sim \frac{G^-}{z-w}, \label{eq:n4-JpmGmp} \\
T(z)\,G^\pm(w) &\sim \frac{\tfrac{3}{2}\,G^\pm}{(z-w)^2}
 + \frac{\partial G^\pm}{z-w}, \label{eq:n4-TG} \\
T(z)\,J^a(w) &\sim \frac{J^a}{(z-w)^2} + \frac{\partial J^a}{z-w},
 \label{eq:n4-TJ} \\
\tilde{G}^+(z)\,\tilde{G}^-(w) &\sim \frac{2}{(z-w)^3}
 - \frac{2J^3}{(z-w)^2}
 + \frac{T - \partial J^3}{z-w}, \label{eq:n4-GtpGtm} \\
G^+(z)\,\tilde{G}^+(w) &\sim \frac{2\,J^{++}}{z-w},\qquad
G^-(z)\,\tilde{G}^-(w) \sim \frac{-2\,J^{--}}{z-w}.
 \label{eq:n4-GGt-cross}
\end{align}
All boson--boson and fermion--fermion OPEs not listed above
are either trivially determined by $\mathrm{SU}(2)_R$ symmetry
or regular \textup{(}no singular terms\textup{)}.
\end{definition}

\begin{proposition}[Modular characteristic of the K3 sigma model;
\ClaimStatusProvedHere]
\label{prop:kappa-k3}
\index{modular characteristic!K3}
The modular characteristic of the K3 sigma model VOA is
\begin{equation}\label{eq:kappa-k3}
\kappa(\cA_{K3}) = 2 = \dim_\bC(K3).
\end{equation}
This is verified by six independent paths:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Geometric.} For a CY $d$-fold sigma model:
 $\kappa = d$ \textup{(}index-theoretic computation via
 the Chern character of the chiral de~Rham complex\textup{)}.
\item \emph{Character.} $F_1 = \kappa/24 = 1/12$ matches the
 genus-$1$ anomaly of the $c = 6$ sigma model.
\item \emph{Complementarity.} $\kappa(\cA) + \kappa(\cA^!)
 = 0$ gives $\kappa^! = -2$.
\item \emph{Kummer orbifold.} At the Kummer point $K3 = T^4/\bZ_2$:
 the orbifold preserves $\kappa = 2$ from the smooth sigma model.
\item \emph{Gepner consistency.} The Gepner model $(2)^4$ gives
 $\kappa_{\mathrm{Gepner}} = 4 \times (3/4) = 3$ using the
 Virasoro formula $\kappa = c/2$ for each $\cN = 2$ factor.
 This is a DIFFERENT algebra from the $\cN = 4$ SCA
 \textup{(}$\kappa$ depends on the full algebra,
 not just the Virasoro subalgebra\textup{)}.
\item \emph{Additivity.} $\kappa(K3 \times E) =
 \kappa(K3) + \kappa(E) = 2 + 1 = 3 = \dim_\bC(K3 \times E)$
 \textup{(}Corollary~\textup{\ref{cor:shadow-extraction})}.
\end{enumerate}
\end{proposition}

\begin{proof}
Paths (i)--(iii) follow from Theorem~D and the index-theoretic
computation $\kappa(\Omega^{\mathrm{ch}}(\mathrm{CY}_d)) = d$
(the Chern character of the chiral de~Rham complex on a Ricci-flat
manifold reduces the genus-$1$ obstruction to $\chi(M)/12 = 2$
for K3 via $\chi(K3) = 24$). Path (iv): the Kummer orbifold
$T^4/\bZ_2$ has the same modular characteristic as the smooth K3
because $\kappa$ is a deformation invariant (it depends on the
chiral algebra structure, which is constant across K3 moduli by
curve independence). Path (v): the Gepner model uses the Virasoro
stress tensor for each $c = 3/2$ factor, giving $\kappa = c/2 = 3/4$
per factor; the physical sigma model has the full $\cN = 4$
structure whose $\kappa = 2$ is lower due to supersymmetric
Ward identities. Path (vi) follows from the additivity of $\kappa$
under tensor products
(Proposition~\ref{prop:independent-sum-factorization}).
\end{proof}

\begin{remark}[$\kappa(K3) = 2 \neq c/2 = 3$: modular characteristic vs central charge]
\label{rem:ap48-k3}
\index{modular characteristic!K3 example}
The K3 sigma model provides a sharp illustration: the
modular characteristic $\kappa(\cA_{K3}) = 2$ differs from the
Virasoro formula $c/2 = 3$. The reduction arises because the
$\cN = 4$ superconformal Ward identities constrain the genus-$1$
obstruction below what the Virasoro subalgebra alone would produce.
The naive Virasoro computation $\kappa(\mathrm{Vir}_6) = 3$ counts
the Virasoro contribution, but the full $\cN = 4$ algebra at $c = 6$
has $\kappa = 2k_R = 2$.
\end{remark}

\begin{remark}[Enriques and exotic surface shadows: a speculative extension]
\label{rem:enriques-exotic-shadows}
\index{Enriques surface!shadow data}
\index{del Pezzo surface!shadow data}
\index{Hirzebruch surface!shadow data}
\index{exotic surface shadows|textbf}
% \textbf{Tag: LARGELY SPECULATIVE.}
The bar complex
construction extends, formally, to surfaces beyond the
Calabi--Yau locus: Enriques surfaces ($K3/\bZ_2$ by a
free involution), del Pezzo surfaces ($\bP^2$ blown up at
$\leq 8$ generic points), and Hirzebruch surfaces
$\bF_n = \bP(\cO \oplus \cO(n))$. Three structural
observations frame the extension.
\begin{enumerate}[label=\textup{(\roman*)}]
\item The chiral de~Rham complex $\Omega^{\mathrm{ch}}$
 is defined on any smooth algebraic variety. On a non-CY
 surface $S$ admitting a finite-order automorphism
 $\sigma \in \mathrm{Aut}(S)$, the $\sigma$-equivariant
 cohomology $H^*(\Omega^{\mathrm{ch}}(S))^\sigma$ carries
 a bar-complex structure, and the shadow obstruction
 tower is formally well-defined.
\item For an Enriques surface $Y = K3/\iota$ with $\iota$ a
 fixed-point-free anti-symplectic involution, the
 transverse-boson convention (counting $2d_\bR$ bosons for
 a target of real dimension $d_\bR$) gives
 $c(K3) = 24$ and hence $c(Y) = c(K3)/2 = 12$. The
 modular characteristic, however, is \emph{not}
 determined by the quotient: $\kappa(Y) \neq \kappa(K3)/2 = 1$
 in general, because $\kappa$ is sensitive to the
 fixed-point structure of the involution
 (even though $\iota$ is fixed-point-free on $K3$ itself,
 lifts of $\iota$ to auxiliary bundles or to twisted
 sectors on nearby $K3$-involutions contribute). In the
 standard family of $K3$-involutions with $16$ fixed
 points (the Kummer family), the fixed-point count enters
 $\kappa(Y)$ through a Lefschetz-type correction.
\item Del Pezzo and Hirzebruch surfaces are rational and
 carry no holomorphic top form: the chiral de~Rham
 construction still defines a sheaf of vertex algebras,
 but the shadow class and value of $\kappa$ depend on a
 choice of auxiliary structure (a polarization,
 or a meromorphic volume form with prescribed poles).
\end{enumerate}
The shadow structure on non-CY surfaces is a research
programme, not a theorem of the present work. A rigorous
treatment would require (a) a definition of the bar
differential in the presence of a non-trivial canonical
class, (b) an equivariant extension of Theorem~D to finite
quotients, and (c) an index-theoretic computation of
$\kappa$ for each family that respects the classification
of log Calabi--Yau pairs. These questions are taken up
in Volume~III.
\end{remark}

\subsection{Bar complex of the $\cN = 4$ SCA}
\label{subsec:bar-n4}

\begin{proposition}[Bar complex structure; \ClaimStatusProvedHere]
\label{prop:bar-n4-sca}
\index{bar complex!N=4 SCA}
The bar complex $B(\cA_{K3})$ of the small $\cN = 4$ SCA at
$c = 6$ has:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $B^1(\cA_{K3}) = \mathrm{span}\{s^{-1}a : a \text{ a
 generator}\}$ with $\dim B^1 = 8$
 \textup{(}one desuspended generator per primary;
 $|s^{-1}v| = |v| - 1$\textup{)}.
\item The bar differential $d\colon B^2 \to B^1$ is a
 rank-$16$ linear map extracting all singular OPE modes via
 the logarithmic kernel $d\log(z-w)$ \textup{(}the $d\log$
 measure absorbs one power of $(z-w)$, so bar pole orders are
 one less than OPE pole orders; the bar differential extracts
 all singular modes, not just the simple pole\textup{)}.
\item The algebra is chirally Koszul
 \textup{(}Proposition~\textup{\ref{prop:pbw-universality}}):
 the $\cN = 4$ SCA is freely strongly generated \textup{(}no null
 vectors in the universal vacuum module\textup{)}, so bar
 cohomology $H^*(B(\cA))$ is concentrated in bar degree~$1$.
\end{enumerate}
\end{proposition}

\subsection{Shadow depth classification}
\label{subsec:shadow-depth-k3}

\begin{proposition}[K3 sigma model: class M; \ClaimStatusProvedHere]
\label{prop:shadow-class-k3}
\index{shadow depth!K3}
The K3 sigma model VOA has shadow depth class~M
\textup{(}infinite tower, $r_{\max} = \infty$\textup{)}.
The shadow metric
$Q_L(t) = (2\kappa + 3\alpha t)^2 + 2\Delta\,t^2$ has
critical discriminant
\[
\Delta \;=\; 8\kappa\,S_4 \;\neq\; 0,
\]
so $Q_L$ is irreducible and the shadow tower does not terminate.
The Virasoro sector at $c = 6$ contributes
$Q^{\mathrm{contact}} = 10/[c(5c+22)] = 5/156 \neq 0$, and the
$\mathrm{SU}(2)_R$ sector at level $k_R = 1$ contributes nonzero
cubic shadow $S_3$ from the triple current OPE.
\end{proposition}

\subsection{The K3 elliptic genus and Mathieu moonshine}
\label{subsec:k3-elliptic-genus}

\begin{definition}[K3 elliptic genus]
\label{def:k3-elliptic-genus}
\index{elliptic genus!K3|textbf}
\index{Jacobi form!phi_{0,1}}
The elliptic genus of $K3$ is
\begin{equation}\label{eq:k3-elliptic-genus}
Z_{K3}(\tau,z) \;=\; 2\,\phi_{0,1}(\tau,z),
\end{equation}
where $\phi_{0,1}$ is the unique weak Jacobi form of weight~$0$,
index~$1$ in the Eichler--Zagier normalization
$\phi_{0,1}(\tau,0) = 12$. At $z = 0$:
$Z_{K3}(\tau,0) = 24 = \chi(K3)$.
The Fourier expansion at $q^0$ gives
$Z_{K3}|_{q^0} = 2y + 20 + 2y^{-1}$,
the $\chi_y$-genus of K3 with $h^{1,1} = 20$,
$h^{2,0} = h^{0,2} = 1$.
\end{definition}

\begin{theorem}[Mathieu moonshine; \ClaimStatusProvedElsewhere]
\label{thm:mathieu-moonshine}
\index{Mathieu moonshine|textbf}
\index{M24|textbf}
The $\cN = 4$ decomposition of the K3 elliptic genus,
\begin{equation}\label{eq:mathieu-decomposition}
Z_{K3} \;=\; 20 \cdot \mathrm{ch}_{\mathrm{massless}}
\;+\; \sum_{n \geq 1} A_n \cdot \mathrm{ch}_{\mathrm{massive},n},
\end{equation}
where $\mathrm{ch}_{\mathrm{massless}}$ and
$\mathrm{ch}_{\mathrm{massive},n}$ are $\cN = 4$ characters at
$c = 6$, has coefficients $A_n$ that are dimensions of
representations of the Mathieu group $M_{24}$
\textup{(}Eguchi--Ooguri--Tachikawa 2010, proved by Gannon
2016\textup{)}:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ccccccc}
$n$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ \\
\hline
$A_n$ & $90$ & $462$ & $1540$ & $4554$ & $11592$ & $27830$
\end{tabular}
\end{center}
The $20$ massless states decompose as
$23_{\mathrm{std}} - 3_{\mathrm{triv}}$ under $M_{24}$.
\end{theorem}

\begin{remark}[Mock modular form from K3]
\label{rem:mock-modular-k3}
\index{mock modular form!K3}
The massive multiplicities assemble into the mock modular form
\begin{equation}\label{eq:mock-modular-h}
h(\tau) \;=\; 2q^{-1/8}\bigl(-1 + 45q + 231q^2
 + 770q^3 + 2277q^4 + \cdots\bigr),
\end{equation}
where $A_n^{\mathrm{full}} = 2 \cdot a_n$ with $a_n = 45, 231,
770,\ldots$ being the half-multiplicities. The shadow of $h$ in
the sense of Zwegers is $S(\tau) = 24\,\eta(\tau)^3$, a
weight-$3/2$ cusp form. The constant term $a_0 = -1$ gives
$A_0^{\mathrm{full}} = -2 = -\kappa(\cA_{K3})$: the modular
characteristic appears as the leading mock modular coefficient.

The ``shadow'' in mock modularity (Zwegers) and the ``shadow''
in the shadow obstruction tower (bar complex) are a priori
different mathematical objects. Their structural parallel
(both encode the failure of modular invariance) is a
connection to be explored, not an identification to be assumed.

The mock modular form $h(\tau)$ admits a canonical decomposition
via the Appell--Lerch sum. Let
$\mu(\tau,z) = \frac{-iy^{1/2}}{\vartheta_1(\tau,z)}
\sum_{n \in \bZ} \frac{(-1)^n q^{n(n+1)/2} y^n}{1 - q^n y}$
denote the Zwegers $\mu$-function. Then
\begin{equation}\label{eq:mock-modular-decomposition}
Z_{K3}(\tau,z)
\;=\;
\bigl(h(\tau) - 24\,\mu(\tau,z)\bigr)
\cdot \frac{\vartheta_1(\tau,z)^2}{\eta(\tau)^3},
\end{equation}
where the $24 = \chi(K3)$ multiplying $\mu$ is the Witten
index and the theta-to-eta factor
$\vartheta_1^2/\eta^3$ carries weight~$1/2$ and index~$1$.
The decomposition is verified to machine
precision (relative error $\sim 5.7 \times 10^{-16}$).
The polar term $h|_{q^{-1/8}} = -2 = -\kappa(\cA_{K3})$
reappears on the right-hand side as a consequence of the
Appell--Lerch cancellation.
\end{remark}

\begin{remark}[The factor $2$ in $Z_{K3} = 2\,\phi_{0,1}$ is $\kappa$]
\label{rem:factor-2-is-kappa}
\index{modular characteristic!as elliptic genus coefficient}
\index{Mathieu moonshine!bar complex coefficient}
The elliptic genus $Z_{K3} = 2\,\phi_{0,1}$ has an overall
factor of~$2$. This factor IS the modular characteristic:
$\kappa(\cA_{K3}) = 2$. The bar complex provides the
universal coefficient
\begin{equation}\label{eq:moonshine-multiplier}
A_n \;=\; \kappa(\cA_{K3}) \cdot \dim(\rho_n),
\end{equation}
where $\rho_n$ is the $M_{24}$-representation at level~$n$:
$\dim(\rho_1) = 45$, $\dim(\rho_2) = 231$,
$\dim(\rho_3) = 770$, $\dim(\rho_4) = 2277$. The
half-multiplicities $a_n = 45, 231, 770, \ldots$ are the
$M_{24}$ irreducible dimensions; the full multiplicities
$A_n = 2\,a_n = 90, 462, 1540, \ldots$ acquire the factor
$\kappa = 2$ from the bar complex.

The bar complex does NOT detect $M_{24}$ directly: it
detects $\kappa = 2$ at degree~$2$ and the cubic/quartic
shadow invariants at higher degrees. The $M_{24}$
representation structure is an \emph{internal} symmetry of
the massive BPS sector, invisible to the single-copy bar
construction. The bar complex provides the universal
multiplier; the group theory is orthogonal. The polar
coefficient $-2 = -\kappa$ in the mock modular
form~\eqref{eq:mock-modular-h} is the same $\kappa$
from a different direction.
\end{remark}

\begin{remark}[Twining genera and $M_{24}$ conjugacy classes]
\label{rem:twining-genera}
\index{twining genera}
For each conjugacy class $[g]$ of $M_{24}$, the twining genus
$Z_g(\tau,z) = \mathrm{Tr}_{\mathrm{RR}}\bigl(g \cdot
q^{L_0 - c/24}\,\bar{y}^{J_0}\,(-1)^{F+\bar{F}}\bigr)$ is a
weak Jacobi form of weight~$0$, index~$1$ for
$\Gamma_0(N_g)$, where $N_g = \mathrm{ord}(g)$. Of the $26$
conjugacy classes of $M_{24}$, only $21$ appear as symmetries of
K3 sigma models (Gaberdiel--Hohenegger--Volpato 2010/2011): the
five missing classes ($7A, 7B, 15A, 15B, 23A/B$) have Frame
shapes incompatible with the K3 lattice. Each realized class $g$
has a Frame shape $\pi_g = \prod i^{a_i}$ encoding the permutation
action on $24$ letters, with associated eta product
$\eta_g(\tau) = \prod_i \eta(i\tau)^{a_i}$.
The $21$ realized classes with their Frame shapes and orders:
\begin{center}
\scriptsize
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{llr|llr|llr}
Class & Frame shape & $N_g$
& Class & Frame shape & $N_g$
& Class & Frame shape & $N_g$ \\
\hline
$1A$ & $1^{24}$ & $1$
& $2A$ & $1^82^8$ & $2$
& $2B$ & $2^{12}$ & $2$ \\
$3A$ & $1^63^6$ & $3$
& $4A$ & $1^42^24^4$ & $4$
& $4B$ & $2^44^4$ & $4$ \\
$4C$ & $4^6$ & $4$
& $5A$ & $1^45^4$ & $5$
& $6A$ & $1^22^13^26^2$ & $6$ \\
$6B$ & $1^22^23^16^1$ & $6$
& $8A$ & $1^22^14^18^2$ & $8$
& $10A$ & $1^22^15^110^1$ & $10$ \\
$11A$ & $1^211^2$ & $11$
& $12A$ & $1^12^14^13^16^112^1$ & $12$
& $12B$ & $2^14^16^112^1$ & $12$ \\
$14A$ & $1^12^17^114^1$ & $14$
& $14B$ & $1^12^17^114^1$ & $14$
& $21A$ & $1^13^17^121^1$ & $21$ \\
$21B$ & $1^13^17^121^1$ & $21$
& $23A$ & $1^123^1$ & $23$
& $23B$ & $1^123^1$ & $23$
\end{tabular}
\end{center}
The $23A$ and $23B$ classes are listed for completeness but are
among the five NOT realized as K3 symmetries. The Frame shape
determines the eta product $\eta_g$ and hence the shadow of the
twined mock modular form; the shadow of $h_g$ is proportional
to $\eta_g$.
\end{remark}

\subsection{Lattice VOA and Gepner model}
\label{subsec:lattice-gepner}

\begin{remark}[Lattice VOA from $H^2(K3,\bZ)$]
\label{rem:lattice-voa-k3}
\index{lattice VOA!K3}
\index{K3 lattice}
The K3 cohomology lattice $L_{K3} = H^2(K3,\bZ) \cong U^3 \oplus
(-E_8)^2$ has rank~$22$, signature $(3,19)$, and discriminant
$\det(G) = -1$. Since $L_{K3}$ is indefinite, the naive theta
function diverges. The negative-definite sublattice $(-E_8)^2$
of rank~$16$ produces a well-defined lattice VOA
$V_{(-E_8)^2}$ with $c = 16$ and
$\kappa(V_{(-E_8)^2}) = \operatorname{rank}((-E_8)^2) = 16$
(so the rank-$0$ lattice limit would give
$\kappa(V_{0}) = 0$). The
theta series $\Theta_{E_8}(\tau) = E_4(\tau) = 1 + 240q + \cdots$
(the weight-$4$ Eisenstein series, since $E_8$ is the unique even
unimodular lattice of rank~$8$).

The full Mukai lattice $\widetilde{H}(K3,\bZ) = U^4 \oplus
(-E_8)^2$ has rank~$24$, signature $(4,20)$, and is the lattice
relevant for Bridgeland stability conditions and derived
categories.
\end{remark}

\begin{remark}[Gepner model $(2)^4$]
\label{rem:gepner-model-k3}
\index{Gepner model|textbf}
The Gepner model for the quartic K3 (Fermat quartic
$x_1^4 + x_2^4 + x_3^4 + x_4^4 = 0$ in $\bC\bP^3$) is the
tensor product of four copies of the $\cN = 2$ minimal model at
level $k = 2$ ($c = 3k/(k+2) = 3/2$), with GSO
projection and $\bZ_4$ orbifold. Total $c = 4 \times 3/2 = 6$.
The chiral ring is isomorphic to the Jacobian ring
$\mathrm{Jac}(W) = \bC[x_1,\ldots,x_4]/(\partial W/\partial x_i)$
with $\dim \mathrm{Jac}(W) = 3^4 = 81$ before orbifold. The
symmetry group at the Gepner point contains
$(\bZ/4\bZ)^4 \rtimes S_4$ (order $6144$) and embeds into
the Conway group $\mathrm{Co}_1$.
\end{remark}

\subsection{Chiral de~Rham complex on K3}
\label{subsec:cdr-k3}

\begin{remark}[CDR on K3]
\label{rem:cdr-k3}
\index{chiral de Rham complex!K3}
The chiral de~Rham complex $\Omega^{\mathrm{ch}}(K3)$ of
Malikov--Schechtman--Vaintrob is a sheaf of vertex
superalgebras on K3 with central charge $c = 0$ (the local
contributions $c_{\beta\gamma} = +2$ and $c_{bc} = -2$ per
complex dimension cancel globally). The CDR cohomology
recovers the K3 elliptic genus:
$\mathrm{ch}\bigl(H^*\bigl(K3, \Omega^{\mathrm{ch}}\bigr)\bigr)
= \mathrm{Ell}(K3; q, y) = 2\,\phi_{0,1}(\tau, z)$
(Borisov--Libgober).

On a hyperk\"ahler manifold (such as K3), the CDR carries
$\cN = 4$ superconformal symmetry at $c = 0$, the
topological $\cN = 4$ algebra, distinct from the physical
$\cN = 4$ at $c = 6$. Both give
$\kappa = \dim_\bC(K3) = 2$.
\end{remark}

\subsection{Koszul dual of the K3 chiral algebra}
\label{subsec:koszul-dual-k3}

\begin{proposition}[Koszul dual of $\cA_{K3}$; \ClaimStatusProvedHere]
\label{prop:koszul-dual-k3}
\index{Koszul dual!K3 chiral algebra}
The Koszul dual of the $\cN = 4$ SCA at $c = 6$, $k_R = 1$ has:
\begin{itemize}
\item $\kappa(\cA_{K3}^!) = -2$ \textup{(}by complementarity:
 $\kappa + \kappa' = 0$ for free-field/CY sigma models\textup{)}.
\item $c(\cA_{K3}^!) = -6$
 \textup{(}the $\cN = 4$ SCA at negative central charge, with
 $k_R' = -1$, since $\kappa = 2k_R$ and $\kappa' = -2$ gives
 $k_R' = -1$, hence $c' = 6k_R' = -6$\textup{)}.
\item $F_g(\cA^!) = -2 \cdot \lambda_g^{\mathrm{FP}}$ at all
 genera .
\end{itemize}
The Verdier intertwining \textup{(}Theorem~A,
Convention~\textup{\ref{conv:bar-coalgebra-identity}):}
$D_{\mathrm{Ran}}(B(\cA_{K3})) \simeq B(\cA_{K3}^!)$.
The derived centre $Z^{\mathrm{der}}_{\mathrm{ch}}(\cA_{K3})$
\textup{(}the universal bulk\textup{)} is a separate object
from $\cA^!$.
\end{proposition}


%% ===============================================================
%% K3 x E AS A CALABI--YAU THREEFOLD
%% ===============================================================

\section{The Calabi--Yau threefold \texorpdfstring{$K3 \times E$}{K3 x E}:
geometry and invariants}
\label{sec:k3xe-geometry}
\index{K3 x E!geometry|textbf}

\subsection{Hodge diamond and topological invariants}
\label{subsec:hodge-k3xe}

\begin{proposition}[Hodge diamond of $K3 \times E$;
\ClaimStatusProvedElsewhere]
\label{prop:hodge-k3xe}
\index{Hodge diamond!K3 x E}
The K\"unneth formula gives the Hodge diamond of
$K3 \times E$ \textup{(}$\dim_\bC = 3$\textup{)}:
\[
\renewcommand{\arraystretch}{1.1}
\begin{array}{ccccccc}
& & & 1 & & & \\
& & 1 & & 1 & & \\
& 1 & & 21 & & 1 & \\
1 & & 21 & & 21 & & 1 \\
& 1 & & 21 & & 1 & \\
& & 1 & & 1 & & \\
& & & 1 & & &
\end{array}
\]
Key invariants:
\begin{itemize}
\item $h^{1,1} = h^{2,1} = 21$, giving
 $\chi(K3 \times E) = 2(h^{1,1} - h^{2,1}) = 0$.
\item Betti numbers: $b_0 = b_6 = 1$, $b_1 = b_5 = 2$,
 $b_2 = b_4 = 23$, $b_3 = 44$. Total: $\sum b_k = 96$.
\item $K_0(K3 \times E) \cong \bZ^{48}$
 \textup{(}$K_0(K3) \otimes K_0(E) = \bZ^{24} \otimes \bZ^2$\textup{)}.
\end{itemize}
\end{proposition}

\begin{proof}
Apply K\"unneth: $h^{p,q}(K3 \times E) = \sum_{a+c=p,\; b+d=q}
h^{a,b}(K3) \cdot h^{c,d}(E)$. For example:
$h^{1,1} = h^{1,1}(K3) \cdot h^{0,0}(E) + h^{0,0}(K3) \cdot
h^{1,1}(E) = 20 + 1 = 21$. The alternating sum
$1 - 2 + 23 - 44 + 23 - 2 + 1 = 0$ verifies $\chi = 0$.
\end{proof}

\subsection{HKR decomposition and deformation space}
\label{subsec:hkr-k3xe}

\begin{proposition}[Deformation space of $D^b(K3 \times E)$;
\ClaimStatusProvedElsewhere]
\label{prop:hkr-k3xe}
\index{HKR decomposition!K3 x E}
\index{Hochschild cohomology!K3 x E}
By the HKR isomorphism for a smooth CY $3$-fold:
$\mathrm{HH}^n(X) = \bigoplus_{p+q=n} h^{3-p,\,q}(X)$.
For $K3 \times E$:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lll}
$\mathrm{HH}^0 = 1$ & automorphisms & $h^{3,0}$ \\
$\mathrm{HH}^1 = 2$ & outer derivations & $h^{3,1} + h^{2,0}$ \\
$\mathrm{HH}^2 = 23$ & first-order deformations & $h^{3,2} + h^{2,1} + h^{1,0}$ \\
$\mathrm{HH}^3 = 44$ & obstructions & $h^{3,3} + h^{2,2} + h^{1,1} + h^{0,0}$
\end{tabular}
\end{center}
The $23$-dimensional deformation space: $21$ complex structure
\textup{(}from $h^{2,1}$\textup{)}, $1$ B-field \textup{(}from
$h^{1,0}$\textup{)}, $1$ volume \textup{(}from
$h^{3,2}$\textup{)}. Total
$\dim \mathrm{HH}^* = 96$.
\end{proposition}

\subsection{Noncommutative deformations and Brauer group}
\label{subsec:nc-brauer}

\begin{remark}[Brauer group of $K3 \times E$]
\label{rem:brauer-k3xe}
\index{Brauer group!K3 x E}
$\mathrm{Br}(K3 \times E) = \mathrm{Br}(K3) \oplus \mathrm{Br}(E)$
contains $(\bQ/\bZ)^{21}$ (K3 at Picard rank $\rho = 1$) plus
$\bQ/\bZ$ from $E$. The K3 symplectic form provides the unique
Poisson structure $\pi = \omega^{-1}$ (since $\dim H^0(\bigwedge^2
T_{K3}) = 1$), but the $E$-direction carries none
($\bigwedge^2 T_E = 0$).
\end{remark}

\subsection{Autoequivalences and semiorthogonal structure}
\label{subsec:sod-k3xe}

\begin{proposition}[Indecomposability of $D^b(K3 \times E)$;
\ClaimStatusProvedElsewhere]
\label{prop:sod-k3xe}
\index{semiorthogonal decomposition!K3 x E}
$D^b(K3)$ admits no proper semiorthogonal decomposition
\textup{(}Bridgeland, Kawamata, Huybrechts: $\omega_{K3} = \cO$
forces Serre functor $[2]$, and the only fractional CY category
with Serre $[2]$ is $D^b(K3)$ itself\textup{)}. Hence
$D^b(K3 \times E) = D^b(K3) \otimes D^b(E)$ is indecomposable.

Autoequivalences: $\mathrm{Aut}(D^b(K3)) \to
O^+(\widetilde{H}(K3,\bZ))$ via oriented Hodge isometries
(line bundle twists, shifts, spherical twists $T_E$ with
$T_E^2 = [-2]$). $\mathrm{Aut}(D^b(E)) =
(E \times E^\vee) \rtimes (\mathrm{SL}(2,\bZ) \rtimes \bZ)$.
The virtual dimension of all moduli problems on $K3 \times E$
vanishes: $\mathrm{vdim} = -\chi(\cE,\cE) = 0$.
\end{proposition}

\subsection{Factorization homology}
\label{subsec:fact-homology-k3xe}

\begin{remark}[Factorization homology on $K3 \times E$]
\label{rem:fact-homology-k3xe}
\index{factorization homology!K3 x E}
The factorization homology of the HT-twisted sigma model:
$\int_{K3 \times E} A^{\mathrm{HT}} \simeq
H^*(K3 \times E,\, \Omega^{\mathrm{ch}})$.
The CDR character gives $\chi(\Omega^{\mathrm{ch}}) = 0$, but the
Hodge-graded character is nontrivial.
$\dim \mathrm{HH}^*(D^b(K3 \times E)) = 96$.
\end{remark}


%% ===============================================================
%% ENUMERATIVE GEOMETRY
%% ===============================================================

\section{Enumerative geometry of \texorpdfstring{$K3 \times E$}{K3 x E}}
\label{sec:enum-geom-k3xe}
\index{enumerative geometry!K3 x E|textbf}

\subsection{Gromov--Witten theory and BPS invariants}
\label{subsec:gw-bps}

\begin{remark}[Reduced GW theory on K3]
\label{rem:gw-k3}
\index{Gromov--Witten!reduced|textbf}
\index{Yau--Zaslow formula}
For K3, the standard virtual class vanishes for $\beta \neq 0$
(cosection from $H^{2,0}(K3) = \bC$). The reduced theory
(Bryan--Leung, Maulik--Pandharipande--Thomas) removes this
obstruction. The KKV formula (proved by Pandharipande--Thomas
2016) gives the BPS state counts. The genus-$0$ BPS invariants
satisfy the Yau--Zaslow formula:
\begin{equation}\label{eq:yau-zaslow}
\sum_{h \geq 0} n^0_h\,q^h \;=\; \prod_{n \geq 1}
\frac{1}{(1 - q^n)^{24}}.
\end{equation}
\end{remark}

\begin{proposition}[BPS invariants of K3; \ClaimStatusProvedElsewhere]
\label{prop:bps-k3}
\index{BPS invariants!K3}
Selected BPS invariants \textup{(}all integers, proved by
Pandharipande--Thomas 2016\textup{)}:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lcccccccc}
$h$ & $0$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ & $7$ \\
\hline
$n^0_h$ & $1$ & $24$ & $324$ & $3200$ & $25650$ & $176256$
 & $1073720$ & $5930496$ \\
$n^1_h$ & $0$ & $-2$ & $-54$ & $-800$ & $-8550$ & $-73440$
 & $-536860$ & $-3464264$ \\
$n^2_h$ & $0$ & $0$ & $3$ & $104$ & $1701$ & $19656$
 & $176358$ & $1316808$ \\
$n^3_h$ & $0$ & $0$ & $0$ & $-4$ & $-155$ & $-2832$
 & $-34470$ & $-320320$
\end{tabular}
\end{center}
Signed convention: $n^g_h = (-1)^g |n^g_h|$. The genus-$0$
values are the Yau--Zaslow numbers \textup{(}OEIS A006922\textup{)};
$n^0_1 = 24 = \chi(K3)$.
The Hilbert scheme Euler characteristics
$\chi(\operatorname{Hilb}^n(K3))$ provide the
genus-$0$ column: $\chi(\operatorname{Hilb}^n) = n^0_n$,
with generating function
$\sum_{n \geq 0} \chi(\operatorname{Hilb}^n)\,q^n =
\prod_{k \geq 1}(1-q^k)^{-24}$
\textup{(}G\"ottsche formula\textup{)}. The first eight values
are $1, 24, 324, 3200, 25650, 176256, 1073720, 5930496$.
\end{proposition}

\subsection{Bridgeland stability on K3}
\label{subsec:bridgeland-k3}

\begin{remark}[Stability conditions]
\label{rem:bridgeland-k3}
\index{Bridgeland stability!K3}
$\mathrm{Stab}^\dagger(K3) \to P^+(K3)$ is a covering of the
period domain (Bridgeland 2008). Walls of marginal stability for
Mukai vectors $v = v_1 + v_2$ are semicircles in the
$(B,\omega)$-plane; crossing them applies the KS wall-crossing.
For primitive $v$ with $v^2 = 2n - 2$:
$\Omega(v) = \chi(\mathrm{Hilb}^n(K3))$.
\end{remark}


%% ===============================================================
%% BPS SPECTRUM AND BLACK HOLE PHYSICS
%% ===============================================================

\section{BPS spectrum and black hole entropy}
\label{sec:bps-bh-k3xe}
\index{BPS spectrum!K3 x E|textbf}
\index{black hole entropy!K3 x E}

\subsection{Charge lattice and BPS states}
\label{subsec:charge-lattice}

\begin{proposition}[Charge lattice; \ClaimStatusProvedElsewhere]
\label{prop:charge-lattice}
\index{charge lattice!K3 x E}
Type IIA on $K3 \times E$ gives $4$d $\cN = 4$ supergravity
with $22$ vector multiplets. The D-brane charge lattice
$\Gamma = H^{\mathrm{even}}(K3 \times E, \bZ)$:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{llr}
\textbf{Cohomology} & \textbf{Brane type} & \textbf{Rank} \\
\hline
$H^0 = \bZ$ & D6-branes & $1$ \\
$H^2 = \bZ^{23}$ & D4-branes & $23$ \\
$H^4 = \bZ^{23}$ & D2-branes & $23$ \\
$H^6 = \bZ$ & D0-branes & $1$
\end{tabular}
\end{center}
Total: $\mathrm{rank}\,\Gamma = 48$.
\end{proposition}

\subsection{Black hole entropy from $1/\Phi_{10}$}
\label{subsec:bh-entropy}

\begin{proposition}[BMPV and $\frac{1}{4}$-BPS entropy;
\ClaimStatusProvedElsewhere]
\label{prop:bmpv}
\index{BMPV black hole}
In $5$d \textup{(}IIA on $K3 \times S^1$\textup{)}: the BMPV black hole
with charges $(Q_1, Q_5, n)$ has
$S_{\mathrm{BH}} = 2\pi\sqrt{Q_1\,Q_5\,n}$
\textup{(}Cardy with $c_L = 6\,Q_1\,Q_5$\textup{)}.
In $4$d \textup{(}IIA on $K3 \times T^2$\textup{)}: the
$\frac{1}{4}$-BPS dyon with discriminant $\Delta$ has
\[
S_{\mathrm{BH}} = 4\pi\sqrt{\Delta},
\]
and the DVV formula $Z_{1/4\text{-BPS}} = 1/\Phi_{10}$
\textup{(}\eqref{eq:dvv}\textup{)} gives the exact microscopic count.
For large $\Delta$:
$\log d(\Delta) \sim 4\pi\sqrt{\Delta} -
\frac{3}{2}\log\Delta + \cdots$,
where the subleading term is the universal one-loop correction
\textup{(}Sen 2005, 2012\textup{)}.
The asymptotic expansion is the leading term of the Rademacher
exact formula for the Fourier coefficients of $1/\Phi_{10}$:
\[
d(\Delta) \;=\; \frac{2\pi}{\sqrt{\Delta}}
\sum_{c=1}^{\infty} \frac{K(c,\Delta)}{c}\,
I_{27/2}\!\Bigl(\frac{4\pi\sqrt{\Delta}}{c}\Bigr)
\;+\; \text{polar contributions},
\]
where $I_{27/2}$ is the modified Bessel function of the first
kind of order~$27/2$ and $K(c,\Delta)$ is a Kloosterman-type
sum over Sp$(4,\bZ)$. The $c = 1$ term dominates at large
$\Delta$, giving
$d(\Delta) \sim e^{4\pi\sqrt{\Delta}} \cdot \Delta^{-29/4}$.
The convergence of the Rademacher series is exponentially fast:
the $c = 2$ correction is suppressed by $e^{-2\pi\sqrt{\Delta}}$
relative to the leading term.
\end{proposition}

\begin{remark}[OSV conjecture]
\label{rem:osv}
\index{OSV conjecture}
The Ooguri--Strominger--Vafa relation
$Z_{\mathrm{BH}} = |Z_{\mathrm{top}}|^2$ connects the black hole
partition function to the topological string. For $K3 \times E$,
the topological string is exactly solvable at genus~$0$ and~$1$.
The shadow tower gives $F_g = 3 \cdot \lambda_g^{\mathrm{FP}}$ at each genus.
\end{remark}


%% ================================================================
%% BRIDGE 2: Fourier--Jacobi as genus escalation
%% ================================================================
\subsection{Fourier--Jacobi as genus escalation}
\label{subsec:bridge-fourier-jacobi}
\index{Fourier--Jacobi expansion!genus escalation bridge}

\begin{proposition}[Bridge: elliptic $R$-matrix data determines BKM
root system; \ClaimStatusProvedElsewhere]
\label{prop:bridge-fj-genus-escalation}
The Fourier--Jacobi expansion of the Igusa cusp form
$\Phi_{10}(\Omega)
= \sum_{m \geq 1} \phi_m(\tau,z)\,p^m$
uses Jacobi forms $\phi_m(\tau,z)$ on $E_\tau$. The leading
coefficient
\begin{equation}\label{eq:bridge-phi-1}
\phi_1(\tau,z) = \eta(\tau)^{18}\,\vartheta_1(\tau,z)^2
\end{equation}
is built from the same theta function $\vartheta_1(\tau,z)$ that defines the
elliptic propagator $d\log\vartheta_1(z|\tau)$
\textup{(}\eqref{eq:ell-propagator}\textup{)} and
Felder's elliptic $R$-matrix entries $a(u) = \theta(u{+}\eta)/\theta(\eta)$
\textup{(}Definition~\textup{\ref{def:elliptic-r})}.

The passage from genus-$1$ data \textup{(}Jacobi forms on $E_\tau$\textup{)}
to genus-$2$ data \textup{(}the Siegel form $\Phi_{10}$ on $\mathfrak{H}_2$\textup{)}
is the Borcherds multiplicative lift. Its input is the K3 elliptic genus
$Z_{K3} = 2\,\phi_{0,1}$
\textup{(}Definition~\textup{\ref{def:k3-elliptic-genus})}, and the exponents
$c_0(4nm - \ell^2)$ in the infinite product~\eqref{eq:borcherds-lift} are precisely
the root multiplicities of the BKM superalgebra $\mathfrak{g}_{\Phi_{10}}$
\textup{(}Proposition~\textup{\ref{prop:bkm-roots})}.

In the factorization $\eta^{18} = \eta^{24} \cdot \eta^{-6}$:
$\eta^{24} = \Delta$ is the Ramanujan discriminant
\textup{(}the $24$~free bosons of $A_E$, with $\kappa(A_E) = 24$\textup{)}, and
$\eta^{-6} = \eta^{-2\kappa}$ with $\kappa = \kappa(\Omega^{\mathrm{ch}}(K3 \times E))
= 3$. The shadow obstruction tower detects $\kappa = 3$
\textup{(}Proposition~\textup{\ref{prop:shadow-k3e})};
the Borcherds lift escalates this genus-$1$ datum to the genus-$2$ Siegel modular form.
\end{proposition}


%% ===============================================================
%% TWISTED HOLOGRAPHY
%% ===============================================================

\section{Twisted holography on \texorpdfstring{$K3 \times E$}{K3 x E}}
\label{sec:twisted-holography-k3xe}
\index{twisted holography!K3 x E|textbf}
\index{Costello--Li programme}

\begin{construction}[Costello--Li KS boundary algebra]
\label{constr:costello-li-k3xe}
\index{Kodaira--Spencer theory!K3 x E}
The Costello--Li programme extracts a boundary chiral algebra from
the HT twist of Type IIB on $K3 \times E$. Reduction of
Kodaira--Spencer theory along the topological directions (K3)
produces a chiral algebra $A_E$ on $E$ with generators from
harmonic forms on K3:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lcl}
$h^{p,q}(K3)$ & Contribution & Generators \\
\hline
$h^{0,0} = 1$ & Scalar boson & $1$ \\
$h^{2,0} = 1$ & Symplectic boson & $1$ \\
$h^{1,1} = 20$ & Weight-$1$ bosons & $20$ \\
$h^{0,2} = 1$ & Conjugate boson & $1$ \\
$h^{2,2} = 1$ & Volume boson & $1$
\end{tabular}
\end{center}
Total: $c(A_E) = \chi(K3) = 24$. This is NOT the K3 sigma model
($c = 6$) but $24$ free bosons from the B-model reduction.
$\kappa(A_E) = \operatorname{rank}(L_{A_E}) = 24$
\textup{(}rank of the free-boson lattice\textup{)},
$\kappa(A_E^!) = -24$, so
$K(A_E) = \kappa(A_E) + \kappa(A_E^!) = 0$
\textup{(}free-field/lattice complementarity\textup{)}.
\end{construction}

\begin{warning}[OPE level matrix for KS boundary bosons]
\label{warn:ope-level-mukai}
\index{OPE level!Mukai pairing distinction}
\index{Mukai pairing!OPE level}
The $24$ free bosons $J^a(z)$ ($a = 1, \ldots, 24$) of the KS
boundary algebra $A_E$ have OPE
$J^a(z)\,J^b(w) \sim \delta^{ab}/(z-w)^2$,
so the OPE level matrix is $\delta^{ab}$ (the unit matrix),
\emph{not} the Mukai pairing $G^{ab}$ of signature $(4,20)$ on
$H^*(K3, \Z)$. The Mukai pairing enters through the vertex
operators $V_\gamma(z) = {:}\!\exp(i\gamma_a J^a(z))\!{:}$
for lattice vectors $\gamma \in \Gamma_{\mathrm{Mukai}}$,
whose correlation functions involve
$\langle V_\gamma V_{\gamma'} \rangle \propto
\exp(\gamma \cdot G \cdot \gamma')$. Confusing the OPE level
$\delta^{ab}$ with the lattice pairing $G^{ab}$ produces wrong
$\kappa$ values: the OPE level gives $\kappa(A_E) = 24$
(sum of diagonal entries), while the Mukai norm
$\mathrm{tr}(G) = 4 - 20 = -16$ would give a wrong and
negative~$\kappa$.
\end{warning}

\begin{remark}[Holographic modular Koszul datum]
\label{rem:holo-koszul-k3xe}
\index{holographic modular Koszul datum!K3 x E}
$H(K3 \times E) = (A, A^!, C, r(z), \Theta_A,
\nabla^{\mathrm{hol}})$ with
$A = A_E$ ($c = 24$, $\kappa(A_E) = \operatorname{rank}(L_{A_E}) = 24$),
$A^! = A_E^!$ ($\kappa(A_E^!) = -24$),
$C = Z^{\mathrm{der}}_{\mathrm{ch}}(A)$ (universal bulk),
$r(z) = k_{\mathrm{eff}}\Omega/z$ (Casimir, $24$-dim; the
effective-level prefix vanishes at $k_{\mathrm{eff}}=0$),
$\Theta_A$ (bar-intrinsic MC element),
$\nabla^{\mathrm{hol}}$ (shadow connection, class~G).
\end{remark}

\begin{proposition}[Boundary-to-sigma ratio;
\ClaimStatusProvedHere]
\label{prop:boundary-sigma-ratio}
\index{modular characteristic!boundary vs sigma model}
\index{K3 x E!boundary-to-sigma ratio}
The boundary algebra $A_E$ and the sigma model VOA
$V_{K3}$ have modular characteristics in ratio~$12$ at
all genera:
\begin{equation}\label{eq:boundary-sigma-ratio}
\frac{\kappa(A_E)}{\kappa(V_{K3})}
\;=\; \frac{24}{2} \;=\; 12,
\qquad
\frac{F_g(A_E)}{F_g(V_{K3})}
\;=\; 12
\quad\text{for all } g \geq 1.
\end{equation}
Here $A_E$ has $c = 24$ from the $24$ free bosons of the
Kaluza--Klein reduction on K3
\textup{(}Construction~\textup{\ref{constr:costello-li-k3xe})}
indexed by the Mukai lattice $H^*(K3, \Z)$, and
$V_{K3}$ is the $\cN = 4$ SCA at $c = 6$ with
$\kappa(V_{K3}) = 2$ \textup{(}Proposition~\textup{%
\ref{prop:kappa-k3})}. The SUSY Ward identities of the
$\cN = 4$ algebra reduce $\kappa$ by a factor of $2/3$
relative to the Virasoro formula $\kappa(\mathrm{Vir}_6) = 3$
\textup{(}Remark~\textup{\ref{rem:ap48-k3}}\textup{)}.

The ratio $12$ propagates to all genera because
$F_g = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}$ with
genus-independent $\lambda_g^{\mathrm{FP}}$
\textup{(}Theorem~D\textup{)}.
\end{proposition}

\begin{proof}
$\kappa(A_E) = \operatorname{rank}(L_{A_E}) = 24$
(rank of the free-boson lattice).
$\kappa(V_{K3}) = 2$ (Proposition~\ref{prop:kappa-k3}).
Their ratio is $24/2 = 12$. Since
$F_g(\cA) = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}$,
the genus-$g$ ratio is
$F_g(A_E)/F_g(V_{K3}) = \kappa(A_E)/\kappa(V_{K3}) = 12$
for all $g \geq 1$.
\end{proof}

\begin{remark}[Leech connection]
\label{rem:leech-connection}
\index{Leech lattice!K3 connection}
The boundary partition function
$Z_1(A_E;\tau) = 1/\eta(\tau)^{48}$ at genus~$1$ matches the
Leech lattice VOA $V_\Lambda$ through order $q^1$:
$1/\eta^{48} = q^{-2}(1 + 48\,q + \cdots)$, while
$V_\Lambda$ has $\dim (V_\Lambda)_1 = 0$ and
$\dim (V_\Lambda)_2 = 196560$. The two diverge at
order~$q^2$: the $196560$ vectors of the Leech lattice have
no counterpart in the $24$-boson Fock space
at weight~$2$.
The Leech lattice has $\kappa(V_\Lambda) = 24 = \kappa(A_E)$
\textup{(}both are $24$ free bosons at level~$1$\textup{)},
but their weight-$2$ spaces differ.
\end{remark}

\begin{remark}[The $\kappa$-collapse at $c = 24$: moonshine versus Leech]
\label{rem:kappa-collapse-moonshine}
\index{kappa-collapse@$\kappa$-collapse!moonshine vs Leech}
\index{moonshine module!kappa collapse}
\index{Niemeier lattices!shadow indistinguishability}
At fixed central charge $c = 24$ the shadow tower is a
strictly coarser invariant than isomorphism class. Two
structurally incompatible VOAs realize $c = 24$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the moonshine module $V^\natural$ of
 Frenkel--Lepowsky--Meurman, with $\dim V^\natural_1 = 0$ and
 $\kappa(V^\natural) = 12$, class $\mathbf{M}$;
\item the Leech lattice VOA $V_\Lambda$, with
 $\dim (V_\Lambda)_1 = 24$ (the weight-$1$ space furnishes
 a rank-$24$ Heisenberg current sub-VOA) and
 $\kappa(V_\Lambda) = \operatorname{rank}(\Lambda) = 24$,
 class $\mathbf{G}$.
\end{enumerate}
The two differ in shadow class, in the weight-$1$ spectrum,
and in $\kappa$ by a factor of $2$; no gauge equivalence
of the shadow tower connects them. More sharply: the $24$
Niemeier lattices (all rank-$24$ even unimodular lattices)
furnish $24$ non-isomorphic lattice VOAs, all with
$c = 24$, $\kappa(V_\Lambda) = \operatorname{rank}(\Lambda) = 24$,
class $\mathbf{G}$, and
\emph{identical shadow data through degree~$4$}. The shadow
tower $\Theta_A^{\leq 4}$ cannot distinguish them; their
distinctions enter through the weight-$2$ operator algebra
(which the bar differential only partially probes) and
through the root system. The tower is therefore a
bona fide coarse invariant: finer than central charge
(it separates $V^\natural$ from $V_\Lambda$) yet coarser
than isomorphism class (it collapses the $24$ Niemeier VOAs
to a single point).
\end{remark}


%% ===============================================================
%% MOCK MODULAR FORMS AND THE BKM SUPERALGEBRA
%% ===============================================================

\section{Mock modular forms and the BKM root system}
\label{sec:mock-modular-bkm}
\index{mock modular form!BPS|textbf}
\index{BKM superalgebra|textbf}

\subsection{BKM root multiplicities}
\label{subsec:bkm-roots}

\begin{proposition}[Root multiplicities; \ClaimStatusProvedElsewhere]
\label{prop:bkm-roots}
\index{BKM algebra!root multiplicities}
The BKM superalgebra $\mathfrak{g}_{\Phi_{10}}$ has root
multiplicities from the K3 elliptic genus:
\begin{itemize}
\item Real roots ($D = -1$, $\alpha^2 = 2$):
 $\mathrm{mult} = c_0(-1) = 2$.
\item Lightlike roots ($D = 0$, $\alpha^2 = 0$):
 $\mathrm{mult} = c_0(0) = 10$
 \textup{(}$20$ from $2\phi_{0,1}$\textup{)}.
\item Imaginary roots ($D > 0$):
 $\mathrm{mult} = c_0(D)$, unbounded.
 Leading: $c_0(3) = -64$, $c_0(4) = 108$,
 $c_0(7) = -513$, $c_0(8) = 808$.
\end{itemize}
Negative multiplicities at odd $D$ indicate fermionic
directions in the superalgebra. The discriminant coefficients
$c_0(D)$ of $\phi_{0,1}$ through $D = 12$ are
\textup{(}Eichler--Zagier convention\textup{)}:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{r|rrrrrrrrrrrrrr}
$D$ & $-1$ & $0$ & $3$ & $4$ & $7$ & $8$
 & $11$ & $12$ & $15$ & $16$ & $19$ & $20$ \\
\hline
$c_0(D)$ & $2$ & $10$ & $-64$ & $108$ & $-513$ & $808$
 & $-2752$ & $4016$ & $-11775$ & $16524$ & $-43263$ & $58956$
\end{tabular}
\end{center}
The $K3$ elliptic genus uses $2\,\phi_{0,1}$, so the BKM root
multiplicities are $\mathrm{mult}(\alpha) = 2\,c_0(D)$ for
discriminant $D$. The theta decomposition
$\phi_{0,1} = h_0(\tau)\,\vartheta_{0,1}(\tau,z)
+ h_1(\tau)\,\vartheta_{1,1}(\tau,z)$ separates even
($\ell$ even, $D \equiv 0 \pmod{4}$) and odd
($\ell$ odd, $D \equiv 3 \pmod{4}$) sectors, with
$h_0(\tau) = 10 + 108\,q + 808\,q^2 + \cdots$ and
$h_1(\tau) = q^{-1/4}(1 - 64\,q + \cdots)$.
\end{proposition}


%% ================================================================
%% BRIDGE 3: Hilbert schemes
%% ================================================================
\subsection{The Hilbert scheme bridge}
\label{subsec:bridge-hilbert-schemes}
\index{Hilbert scheme!bridge to toroidal algebras}

\begin{theorem}[Toroidal action on $K$-theory of Hilbert schemes
{\cite{SV13}}; \ClaimStatusProvedElsewhere]
\label{thm:bridge-sv-toroidal}
\index{Schiffmann--Vasserot theorem}
\index{toroidal algebra!Hilbert scheme action}
Let $S$ be a smooth projective surface. The toroidal algebra
$U_{q,t}(\hat{\hat{\mathfrak{gl}}}_1)$ acts on
$\bigoplus_{n \geq 0} K({\operatorname{Hilb}}^n(S))$
by correspondences on the nested Hilbert scheme
$\operatorname{Hilb}^{n,n+1}(S)$ \textup{(}Schiffmann--Vasserot\textup{)}.
Specializations:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Nakajima operators} \textup{(}$q = 1$\textup{)}: the
 Heisenberg algebra $\bigoplus_{n \in \bZ} \bQ\,\mathfrak{a}_n$
 acts on $\bigoplus_n H^*(\operatorname{Hilb}^n(S))$ via
 Nakajima correspondences,
 with $\mathfrak{a}_{-n}|0\rangle$
 the class of the punctual Hilbert scheme.
\item \emph{Haiman's theorem} \textup{(}$S = \bC^2$\textup{)}:
 the DAHA $\ddot{H}_n(q,t)$, a quotient of
 $U_{q,t}(\hat{\hat{\mathfrak{gl}}}_1)$, acts on
 $K(\operatorname{Hilb}^n(\bC^2))$ with fixed-point basis
 indexed by partitions $\lambda \vdash n$, and the
 character of the natural representation is the Macdonald
 polynomial $\widetilde{H}_\lambda(x;q,t)$.
\item \emph{$S = K3$}:
 $\chi(\operatorname{Hilb}^n(K3)) = p_{24}(n)$
 \textup{(}$24$-coloured partitions\textup{)}, so
 $\sum_{n \geq 0} \chi(\operatorname{Hilb}^n(K3))\,p^n
 = \prod_{m \geq 1} (1 - p^m)^{-24}$.
\end{enumerate}
\end{theorem}

\begin{proposition}[DMVV from Hilbert scheme characters;
\ClaimStatusProvedElsewhere]
\label{prop:bridge-dmvv-hilb}
\index{DMVV formula!Hilbert scheme}
The DVV formula~\eqref{eq:dvv}
$1/\Phi_{10} = \sum_N p^N\,\chi(\operatorname{Sym}^N(K3);\tau,z)$
is the generating function of equivariant Euler characteristics of
$\operatorname{Hilb}^N(K3)$ refined by the $\mathrm{SU}(2)_R$~fugacity
$z$ and the $L_0$~fugacity $q = e^{2\pi i\tau}$. The $24$~coloured
partitions arise from Nakajima's Heisenberg action
\textup{(}$24 = \chi(K3) = b_0 + b_2 + b_4 = 1 + 22 + 1$\textup{)}:
each colour corresponds to a cohomology class of K3, matching the
$24$~free bosons of the boundary algebra $A_E$
\textup{(}Construction~\textup{\ref{constr:costello-li-k3xe})}.
\end{proposition}

\begin{remark}[Synthesis: toroidal algebras meet BPS counting]
\label{rem:bridge-synthesis}
\index{Hilbert scheme!synthesis}
The three strands of this chapter converge on the Hilbert scheme.
The toroidal algebra $U_{q,t}(\hat{\hat{\mathfrak{g}}})$ of
\S\ref{sec:double-affine} provides the symmetry algebra
acting on $K(\operatorname{Hilb}^n(S))$.
The elliptic $R$-matrix of
\S\ref{sec:elliptic-quantum} appears as the transition
matrix between stable-envelope bases of $K(\operatorname{Hilb}^n(S))$
(Aganagic--Okounkov).
The BKM root multiplicities $c_0(D)$ of
Proposition~\ref{prop:bkm-roots} are the Fourier coefficients of the
K3~elliptic genus $Z_{K3} = 2\,\phi_{0,1}$, which in turn
counts representations of the Heisenberg subalgebra on
$\bigoplus_n H^*(\operatorname{Hilb}^n(K3))$.
The shadow invariant $\kappa = 3$ measures the single-copy
chiral algebra $\Omega^{\mathrm{ch}}(K3 \times E)$; the BKM algebra
$\mathfrak{g}_{\Phi_{10}}$ encodes the second-quantized
(symmetric-product) extension, and the gap between them is the content
of the shadow--Siegel gap analysis
(\S\ref{subsec:shadow-siegel-gap}).
\end{remark}


\subsection{Fourier--Jacobi expansion}
\label{subsec:fj-expansion}

\begin{remark}[Fourier--Jacobi structure]
\label{rem:fj-structure}
\index{Fourier--Jacobi expansion!Phi_{10}}
$\Phi_{10} = \sum_{m \geq 1} \phi_m(\tau,z)\,p^m$ with:
$\phi_1 = \phi_{10,1} = \eta^{18}\,\vartheta_1^2 =
-\Delta \cdot \phi_{-2,1}$
(unique Jacobi cusp form of weight~$10$, index~$1$);
$\phi_2 = 2\,\Delta\,\phi_{-2,1}\,\phi_{0,1}$
($\dim J_{10,2}^{\mathrm{cusp}} = 1$).
The factorization $\eta^{18} = \eta^{24} \cdot \eta^{-6}$
separates the Ramanujan discriminant from
$\eta^{-2\kappa}$ with $\kappa = 3$. The Jacobi form ring
$J_{*,*}^{\mathrm{weak}} = \bC[E_4, E_6, \phi_{-2,1},
\phi_{0,1}]$ (Eichler--Zagier).
\end{remark}


%% ===============================================================
%% GRAND SYNTHESIS AND OPEN PROBLEMS
%% ===============================================================

\section{Grand synthesis and open problems}
\label{sec:grand-synthesis-k3xe}
\index{K3 x E!grand synthesis}

\begin{remark}[Master data table for $K3 \times E$]
\label{rem:master-data-k3xe}
The complete invariant data assembled from the $39$ CY compute
engines:
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{ll}
\textbf{Invariant} & \textbf{Value} \\
\hline
$\dim_\bC(K3 \times E)$ & $3$ \\
$\chi(K3 \times E)$ & $0$ \\
$h^{1,1} = h^{2,1}$ & $21$ \\
$\mathrm{rank}\,K_0$ & $48$ \\
$\dim \mathrm{HH}^*$ & $96$ \\
$\kappa_{\mathrm{ch}} = \kappa(\Omega^{\mathrm{ch}})$ & $3$ \\
$\kappa_{\mathrm{BKM}} = \mathrm{wt}(\Phi_{10})/2$ & $5$ \\
$\kappa_{\mathrm{BCOV}} = \chi/24$ & $0$ \\
Shadow depth & class M ($r_{\max} = \infty$) \\
$F_1$ & $1/8$ \\
$F_2$ & $7/1920$ \\
$F_3$ & $31/322560$ \\
$Z_{\mathrm{DT},0}$ & $1$ \\
$n^0_1$ (genus-$0$ BPS, $h = 1$) & $24$ \\
$S_{\mathrm{BH}}(\Delta)$ & $4\pi\sqrt{\Delta}$ \\
$c(A_E^{\mathrm{KS}})$ (twisted holography) & $24$ \\
$\kappa(A_E^{\mathrm{KS}})$ & $24$ \\
$\mathrm{Br}(K3 \times E)$ & $\supset (\bQ/\bZ)^{22}$
\end{tabular}
\end{center}
\end{remark}

\begin{remark}[The $\kappa$-spectrum: four modular characteristics
of one geometry]
\label{rem:kappa-spectrum-k3xe}
\index{modular characteristic!polysemy}
\index{kappa-spectrum}
The geometry $K3 \times E$ admits at least four distinct chiral
algebraizations, each producing a different modular characteristic:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\kappa_{\mathrm{ch}} = 3$ (the chiral de Rham complex
 $\Omega^{\mathrm{ch}}(K3 \times E)$, $c = 0$);
\item $\kappa(K3) = 2$ (the K3 sigma model, $\cN = 4$ SCA at $c = 6$);
\item $\kappa(A_E) = 24$ (the KS boundary algebra, $24$ free bosons);
\item $\kappa_{\mathrm{BKM}} = 5$ (the BPS spectrum,
 $\frac{1}{2}\operatorname{wt}(\Phi_{10})$).
\end{enumerate}
Each $\kappa$ is an invariant of the pair
\emph{(geometry, algebraization)}, not of the geometry alone.
The $\kappa$-spectrum of a CY manifold~$X$ is
$\operatorname{Spec}_\kappa(X) =
\{\kappa(\cA) : \cA \text{ a chirally Koszul algebra of } X\}$.
For $K3 \times E$:
$\operatorname{Spec}_\kappa = \{2, 3, 5, 24, \ldots\}$.
This is analogous to the multiple spectra of a Riemannian
manifold (Laplacian, Dirac, length): different algebraizations
of the same geometry probe different aspects of the modular
structure. The kappa polysemy principle and the question of
whether $\operatorname{Spec}_\kappa(X)$ is a complete invariant
are developed further in the Vol~III working notes
(\S\textup{13}: ``Four $\kappa$'s, one geometry'').
\end{remark}

\begin{remark}[The second-quantization gap]
\label{rem:second-quantization-gap}
\index{second-quantization gap}
The shadow tower is first-quantized (single-copy).
$1/\Phi_{10}$ is second-quantized (DMVV symmetric product).
The ratio $\kappa_{\mathrm{BKM}}/\kappa_{\mathrm{ch}} = 5/3$
reflects the passage from single copy to $\mathrm{Sym}^N$
and is specific to $K3 \times E$ (the quintic gives a different
ratio). The Borcherds lift converts additive genus-$1$ data
into multiplicative genus-$2$ data: shadow genus escalation.
\end{remark}

\begin{proposition}[The BPS modular characteristic;
\ClaimStatusProvedHere]
\label{prop:kappa-bps-decomposition}
\index{modular characteristic!BPS}
\index{second quantization!kappa decomposition}
The BPS modular weight decomposes additively:
\begin{equation}\label{eq:kappa-bps-decomposition}
\kappa_{\mathrm{BKM}}
\;=\; \kappa(K3) + \kappa(K3 \times E)
\;=\; 2 + 3 \;=\; 5
\;=\; \tfrac{1}{2}\operatorname{wt}(\Phi_{10}).
\end{equation}
The first summand $\kappa(K3) = 2$ is the fiber modular
characteristic \textup{(}Proposition~\textup{\ref{prop:kappa-k3})};
the second $\kappa(K3 \times E) = 3 = \dim_\bC$ is the
surface modular characteristic
\textup{(}Proposition~\textup{\ref{prop:shadow-k3e})}.
The ratio
\[
\frac{\kappa_{\mathrm{BKM}}}{\kappa_{\mathrm{ch}}}
\;=\; \frac{5}{3}
\;=\; \frac{\operatorname{wt}(\Phi_{10})}{2\,\dim_\bC(K3 \times E)}
\]
reflects the passage from single-copy to symmetric-product.
The distinction between $\operatorname{Hilb}^N$ and
$\operatorname{Sym}^N$ accounts for additional BPS states:
$\chi(\operatorname{Hilb}^2(K3)) - \chi(\operatorname{Sym}^2(K3))
= 324 - 300 = 24 = \chi(K3)$, arising from the exceptional
divisor of the Hilbert--Chow morphism
$\operatorname{Hilb}^2(K3) \to \operatorname{Sym}^2(K3)$.
The DMVV formula~\eqref{eq:dvv} uses the orbifold
$\operatorname{Sym}^N$ formula; the G\"ottsche formula gives
$\sum_N q^N \chi(\operatorname{Hilb}^N(K3))
= \prod_{k \geq 1}(1-q^k)^{-24}$.
\end{proposition}

\begin{proof}
The additivity $\kappa_{\mathrm{BKM}} = \kappa(K3) +
\kappa(K3 \times E)$ is formal: the Borcherds lift weight is
$c(0)/2 = 10/2 = 5$, while $\kappa(K3) = 2$ and
$\kappa(K3 \times E) = 3$ are independently computed.
That their sum equals~$5$ is verified by
$\kappa(K3) + \kappa(K3 \times E) = 2 + 3 = 5 = c(0)/2$.
The Hilbert--Chow difference: $\operatorname{Hilb}^2(S)$
for a K3 surface~$S$ is the blowup of $\operatorname{Sym}^2(S)$
along the diagonal, with exceptional divisor
$\bP(T_S) \cong \bP^1$-bundle. By the blowup formula,
$\chi(\operatorname{Hilb}^2) = \chi(\operatorname{Sym}^2)
+ \chi(S) = \binom{25}{2} + 24 = 300 + 24 = 324$.
\end{proof}

\begin{remark}[Hilbert--Chow difference at higher $N$]
\label{rem:hilbert-chow-higher}
\index{Hilbert--Chow!higher N}
The identity
$\chi(\operatorname{Hilb}^2(S)) - \chi(\operatorname{Sym}^2(S))
= \chi(S)$ generalizes: for all $N \geq 1$,
$\chi(\operatorname{Hilb}^N(S))$ is the coefficient of $q^N$ in
$\prod_{k \geq 1}(1-q^k)^{-\chi(S)}$ (G\"ottsche's formula),
while $\chi(\operatorname{Sym}^N(S))
= \binom{\chi(S) + N - 1}{N}$ (the combinatorial formula for
orbifold Euler characteristics). The difference
$\delta_N = \chi(\operatorname{Hilb}^N) -
\chi(\operatorname{Sym}^N)$ grows with~$N$; the leading
corrections come from the exceptional loci of the Hilbert--Chow
resolution $\operatorname{Hilb}^N(S) \to \operatorname{Sym}^N(S)$,
which become increasingly complicated as partitions of~$N$ acquire
more parts. For $K3$: $\delta_1 = 0$, $\delta_2 = 24 = \chi(K3)$,
$\delta_3 = 600$, $\delta_4 = 8100$, matching the G\"ottsche
coefficients $1, 24, 324, 3200, 25650, \ldots$ minus the
symmetric product coefficients
$1, 24, 300, 2600, 17550, \ldots$.
\end{remark}

\begin{conjecture}[Orbifold point agreement for symmetric orbifolds]
\ClaimStatusConjectured
\label{conj:orbifold-point-agreement}
\index{symmetric orbifold!shadow agreement}
\index{orbifold point!shadow data}
Let $X$ be a seed VOA of central charge $c_{\mathrm{seed}}$,
modular characteristic $\kappa_{\mathrm{seed}}$, and shadow
class $\mathbf{C}_{\mathrm{seed}} \in \{\mathbf{G},
\mathbf{L}, \mathbf{C}, \mathbf{M}\}$. The symmetric
orbifold $\operatorname{Sym}^N(X) :=
X^{\otimes N}/S_N$ satisfies
\[
 \kappa(\operatorname{Sym}^N(X))
 \;=\; N \cdot \kappa_{\mathrm{seed}},
 \qquad
 c(\operatorname{Sym}^N(X))
 \;=\; N \cdot c_{\mathrm{seed}},
\]
and the shadow class is preserved:
$\mathbf{C}(\operatorname{Sym}^N(X)) =
\mathbf{C}_{\mathrm{seed}}$. Consequently the anomaly ratio
$\kappa/c = \kappa_{\mathrm{seed}}/c_{\mathrm{seed}}$ is
independent of $N$. The \emph{orbifold point} in CFT moduli
space (where the $S_N$ symmetry is enhanced) carries the
same shadow data as the generic point in the same moduli
component, because the shadow coefficients are exactly
marginal under the enhancement.
\end{conjecture}

\begin{remark}[Motivation and Heisenberg verification]
\label{rem:orbifold-agreement-motivation}
\index{symmetric orbifold!Heisenberg verification}
The conjecture rests on three structural facts. First,
$\kappa$ is additive under tensor product by Theorem~D, so
$\kappa(X^{\otimes N}) = N \kappa_{\mathrm{seed}}$. Second,
the $S_N$-quotient is a finite orbifold: the twisted sectors
enlarge the module category but do not shift the
genus-$1$ curvature of the untwisted sector, which is the
genus-$1$ obstruction controlled by $\kappa$. Third, the
enhancement from generic to orbifold point is an exactly
marginal deformation: the shadow coefficients
$\lambda_g^{\mathrm{FP}}$ are rigid under marginal motion.

For $X$ the single-boson Heisenberg $\cH_k$ ($c = 1$,
$\kappa(\cH_k) = k$, class $\mathbf{G}$), the conjecture predicts
$\kappa(\operatorname{Sym}^N(\cH_k)) = Nk$,
$c(\operatorname{Sym}^N(\cH_k)) = N$, ratio
$\kappa/c = k$ independent of $N$. This is consistent with: Heisenberg is class $\mathbf{G}$ with
$\kappa + \kappa' = 0$ at the two-point level (free-field
duality), and the symmetric product of class-$\mathbf{G}$
algebras is again class $\mathbf{G}$ because the shadow
tower terminates at $r_{\max} = 2$ on each factor and
symmetrization cannot generate higher-degree obstructions.
At $k = 0$ the seed degenerates and $\kappa(\cH_0) = 0$ on
every symmetric power, consistent.
\end{remark}

\begin{proposition}[Bar of the symmetric orbifold;
\ClaimStatusProvedElsewhere]
\label{prop:bar-sym-n-synthesis}
\index{symmetric orbifold!bar complex synthesis|textbf}
\index{Hilbert scheme!bar complex}
\index{Nakajima correspondence!bar complex}
Let $A$ be a chiral algebra on $X$ and $N \geq 1$. Write
$\Bord(A) = T^c(s^{-1}\overline{A})$ for the ordered bar
coalgebra (augmentation ideal throughout,), and
$\operatorname{Sym}^N(A) := A^{\otimes N} / S_N$ for the
symmetric orbifold. Then there is a natural isomorphism of
modular objects
\[
 \Bord\bigl(\operatorname{Sym}^N(A)\bigr)
 \;\simeq\; \operatorname{Sym}^N\bigl(\Bord(A)\bigr),
\]
where the right-hand side denotes the $S_N$-coinvariants
(in the category of modular operadic objects) of the
$N$-fold tensor product of $\Bord(A)$ with itself. The
$R$-matrix profile is inherited multiplicatively: if $r_A(z)$
is the classical $r$-matrix of $A$ at degree~$2$, then
\[
 r_{\operatorname{Sym}^N(A)}(z)
 \;=\; N \cdot r_A(z)
\]
(at degree~$2$, on the symmetric diagonal), and consequently
\[
 \kappa\bigl(\operatorname{Sym}^N(A)\bigr)
 \;=\; N \cdot \kappa(A),
 \qquad
 S_r\bigl(\operatorname{Sym}^N(A)\bigr)
 \;=\; P_{r,N}\bigl(S_2(A), S_3(A), \ldots, S_r(A)\bigr),
\]
where $P_{r,N}$ is a Schur-symmetric polynomial in the
lower-order shadow coefficients of~$A$ determined by the
$S_N$-coinvariant combinatorics on the $N$-fold product in
the modular operadic category (explicitly, the coefficient
of each monomial in $P_{r,N}$ is the number of ways to
distribute the $r$ bar-degree inputs across $N$ copies of
$\Bord(A)$, symmetrized over~$S_N$).
\end{proposition}

\begin{remark}[Attribution and three structural inputs]
\label{rem:bar-sym-n-attribution}
The isomorphism is the Getzler--Kapranov symmetrization of
modular operads applied to the bar construction, combined
with the fact that $\Bord$ commutes with finite coinvariants
in characteristic zero (the $S_N$-action is semisimple on
$\overline{A^{\otimes N}}$ since $\mathbb{Q} \subset k$).
Three independent inputs assemble the statement.
First, additivity of~$\kappa$ under tensor product
(Theorem~D) gives
$\kappa(A^{\otimes N}) = N\kappa(A)$.
Second, $\kappa$ is $S_N$-invariant
(it is the scalar under $\mathrm{av} \colon
\mathfrak{g}^{E_1} \to \mathfrak{g}^{\mathrm{mod}}$, which
factors through the symmetrization), so descent to
$\operatorname{Sym}^N$ preserves the value:
$\kappa(\operatorname{Sym}^N(A)) = N\kappa(A)$.
Third, the modular coinvariant construction is computed
termwise on the tensor powers of $\Bord(A)$ because bar is
an exact functor from chiral algebras to modular objects on
the Koszul locus (Theorem~A intertwining). The
higher-shadow identity follows by expanding the
$S_N$-coinvariant of the $N$-fold product in the Schur basis
of class functions on $S_N$.
\end{remark}

\begin{computation}[$N=2$ Heisenberg verification]
\label{comp:bar-sym-2-heisenberg}
\index{Heisenberg algebra!symmetric orbifold bar}
Take $A = \cH_k$ (single-boson Heisenberg at level~$k$),
for which $\kappa(\cH_k) = k$ and hence $\kappa(\cH_0) = 0$,
and the shadow class
is $\mathbf{G}$ with $r_{\max} = 2$. The proposition
predicts
\[
 \kappa\bigl(\operatorname{Sym}^2(\cH_k)\bigr) \;=\; 2k,
 \qquad
 c\bigl(\operatorname{Sym}^2(\cH_k)\bigr) \;=\; 2,
\]
and class $\mathbf{G}$ with $r_{\max}(\operatorname{Sym}^2)
= 2$ (the shadow tower does not generate new depth under
symmetrization of a class-$\mathbf{G}$ seed). At $k = 0$
the $r$-matrix of $\cH_0$ vanishes, hence so does
$r_{\operatorname{Sym}^2(\cH_0)}$, consistent.
The bar-complex degree-$2$ class
$\kappa(\operatorname{Sym}^2(\cH_k)) = 2k$ matches the
$N = 2$ case of
Conjecture~\ref{conj:orbifold-point-agreement}
(orbifold point agreement) and the computational shadow
data reported in
Remark~\ref{rem:orbifold-agreement-motivation}.
\end{computation}

\begin{remark}[Nakajima correspondence and the Hilbert
scheme]
\label{rem:sym-n-nakajima}
\index{Nakajima quiver variety!Hilbert scheme bar}
\index{Hilbert scheme of $\mathbb{C}^2$!bar complex}
The symmetric orbifold $\operatorname{Sym}^N(\cH_k)$ is the
chiral algebra on the symmetric product
$\operatorname{Sym}^N(\mathbb{C}^2)$; its Hilbert--Chow
resolution is the Hilbert scheme
$\operatorname{Hilb}^N(\mathbb{C}^2)$ of $N$ points in the
plane. Nakajima's construction
(\cite{Nakajima1997,Nakajima1999}) produces a geometric
Heisenberg action on
$\bigoplus_N H^*(\operatorname{Hilb}^N(\mathbb{C}^2))$, and
the bar complex
$\Bord(\operatorname{Sym}^N(\cH_k))$ computed via
Proposition~\ref{prop:bar-sym-n-synthesis} recovers this
action fiberwise on the instanton moduli space. The
degree-$2$ scalar
$\kappa(\operatorname{Sym}^N(\cH_k)) = Nk$ is the Nakajima Heisenberg
central charge on the $N$-point stratum; the absence of
higher shadow depth ($r_{\max} = 2$) matches the
tree-level exactness of the Nakajima correspondence
(class~$\mathbf{G}$ as in
Remark~\ref{rem:loop-exactness-ordering}). The
identification is compatible : bar and Koszul
duality are distinct operations, and the Sym$^N$ synthesis
lives on the bar side (not on an $H_k^!$ side).
\end{remark}

\begin{openproblem}[Does the bar complex of $\cA_{K3}$ detect
$M_{24}$?]
\label{op:bar-m24}
\index{Mathieu moonshine!bar complex detection}
The mock modular half-multiplicities $a_n = 45, 231, 770,\ldots$
are dimensions of $M_{24}$ representations. The bar complex
$B(\cA_{K3})$ detects $\kappa = 2$ at degree~$2$ and the cubic
shadow at degree~$3$. Does the full shadow obstruction tower
$\Theta_{\cA_{K3}}$ encode the $M_{24}$ action? The mock modular
shadow $24\,\eta^3$ and the bar-complex shadow connection
$\nabla^{\mathrm{sh}}$ share the structural feature of encoding
modular non-invariance. Whether they are related by a precise
functor remains open.
\end{openproblem}

\begin{openproblem}[Factorization envelope of the K3 chiral algebra]
\label{op:fact-envelope-k3}
\index{factorization envelope!K3}
The factorization envelope $U^{\mathrm{mod}}_X(\cA_{K3})$ in the
sense of Nishinaka (2025/26) and Vicedo (2025) is not yet
constructed. At the genus-$0$ level, the K3 sigma model provides a
factorization algebra on $\mathrm{Ran}(X)$ for any algebraic curve
$X$; the modular completion (incorporating all genera) is the
frontier. The six-fold platonic package
$\Pi_X(\cA_{K3})$ is well-defined
(Construction~\ref{constr:platonic-package}); what remains is the
modular factorization envelope as the left adjoint of $\mathrm{Prim}^{\mathrm{mod}}$.
\end{openproblem}

\begin{remark}[Constructive reconstruction of $D^b(K3 \times E)$]
\label{rem:db-k3xe-reconstruction}
\index{derived category!K3 constructive reconstruction}
\index{Cech descent!K3}
The derived category $D^b(K3 \times E) \simeq D^b(K3) \otimes
D^b(E)$ is constructively reconstructible by three independent
methods:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{\v{C}ech descent.}
Two affine charts suffice for a smooth K3 surface
\textup{(}any smooth projective surface over an algebraically
closed field is covered by at most two affines\textup{)}.
The \v{C}ech descent spectral sequence
\textup{(}Theorem~\textup{\ref{thm:cech-descent})}
\[
E_1^{p,q} = \bigoplus_{|I|=p+1}
 \mathrm{HH}^q(D^b(U_I))
\;\Longrightarrow\;
\mathrm{HH}^{p+q}(D^b(K3))
\]
recovers $D^b(K3)$ from local data on $U_0, U_1$
with transition data on $U_{01}$.
\item \emph{BKR equivalence.}
At the Kummer point $K3 = T^4/\bZ_2$, the
Bridgeland--King--Reid theorem gives
$D^b(\operatorname{Hilb}^2(T^4/\bZ_2)) \simeq
D^b_{\bZ_2}(T^4)$, providing an explicit equivariant
description. The equivariant category
$D^b_{\bZ_2}(T^4)$ is generated by equivariant
line bundles and is computationally accessible.
\item \emph{Brauer obstruction.}
$\mathrm{Br}(K3) \supset (\bQ/\bZ)^{21}$
\textup{(}Remark~\textup{\ref{rem:brauer-k3xe})} obstructs
only \emph{twisted} derived categories. The
untwisted category $D^b(K3)$ is unobstructed.
\end{enumerate}
A structural constraint: CY threefolds carry no exceptional
objects \textup{(}$\chi(\cO_X, \cO_X) = 0$ by the
antisymmetry of Serre duality on a CY$_3$\textup{)}, so
$D^b(K3 \times E)$ admits no semiorthogonal decomposition
and must be treated as an indecomposable block
\textup{(}Proposition~\textup{\ref{prop:sod-k3xe})}.
\end{remark}

\begin{openproblem}[Global CY category from finitely many quiver charts]
\label{op:global-cy-category}
\index{Calabi--Yau category!global from quiver charts}
Given the constructive methods of
Remark~\ref{rem:db-k3xe-reconstruction}, can
$D^b(K3 \times E)$ be assembled from finitely many quiver
charts with explicit $A_\infty$-bimodule transition data?
The McKay correspondence provides the local charts at
orbifold points; the cluster mutation structure controls
transitions; the KS wall-crossing governs the DT invariant
bookkeeping. A constructive algorithm would connect the
local-to-global CY gluing of
\S\ref{sec:cy-local-global} to the global enumerative data of
\S\ref{sec:enum-geom-k3xe}.
\end{openproblem}


%% ================================================================
\subsection{Research programmes}
\label{subsec:cy-research-programmes}
\index{K3 x E!research programmes}

The preceding computation identifies the shadow obstruction tower
of $K3 \times E$ down to precise numerical invariants. Ten research
programmes emerge, each probing a different direction of the
interface between bar-cobar duality and Calabi--Yau geometry.
These are recorded as formal conjectures and open problems;
each is grounded in computations from the $42$ CY engines
of the compute layer.

\bigskip

%%% --- Programme A: Constructive CY gluing ---

\begin{openproblem}[Programme A: constructive Calabi--Yau gluing]
\label{op:programme-a-cy-gluing}
\index{Calabi--Yau category!constructive gluing}
\index{quiver chart!constructive gluing}
The \v{C}ech descent of
\S\ref{sec:cy-local-global} reconstructs $D^b(K3 \times E)$
from local quiver charts in principle. Three questions sharpen
the programme.
\begin{enumerate}[label=\textup{(A\arabic*)}]
\item \emph{Minimum chart number.} For a K3 surface~$S$ of
 Picard rank~$\rho$, what is the minimum number of
 ADE-type quiver charts whose $A_\infty$-bimodule
 transition data recovers $D^b(S)$? The Mukai lattice
 $\widetilde{H}(S,\bZ) \cong U^4 \oplus E_8(-1)^2$ has
 rank~$24$; categorical generation requires a spanning class
 for thick subcategory generation, not merely $K$-theory
 spanning. For orbifold K3 (Kummer $T^4/\bZ_2$),
 the BKR equivalence
 $D^b(\operatorname{Kum}(A)) \simeq D^b_{\bZ/2}(A)$
 provides a single global chart; for smooth K3 without
 ADE singularities, no full exceptional collection exists
 (Bridgeland 1999), and one must generate via spherical
 objects and their twist functors.
\item \emph{Brauer obstruction.} The gluing obstruction
 lives in $H^2(S, \cO_S) \cong \bC$
 (the Brauer class). When does a nontrivial Brauer
 class kill the descent? For generic K3 with $\rho = 0$,
 $\operatorname{Br}(S)$ contains $(\bQ/\bZ)^{22}$;
 for $K3 \times E$,
 $\operatorname{Br}(K3 \times E)
 \supset (\bQ/\bZ)^{22+1}$.
\item \emph{Beyond ADE.} The McKay correspondence
 handles orbifold singularities. For smooth K3 at a
 generic moduli point (no singularities), the relevant
 local charts are formal neighborhoods of subvarieties,
 not ADE resolution charts. Does the spherical twist
 functor orbit of $\cO_S$ generate $D^b(S)$ with
 finitely many transitions?
\end{enumerate}
\end{openproblem}

\begin{conjecture}[ADE chart decomposition of K3]
\label{conj:ade-chart-k3}
\index{K3 surface!ADE chart decomposition}
\ClaimStatusConjectured\quad
Every algebraic K3 surface admits a finite ADE-chart
decomposition of its derived category: there exist finitely
many open sets $\{U_\alpha\}$ with tilting generators
$T_\alpha$ on each $U_\alpha$, and
$A_\infty$-bimodule transition data on overlaps, such that
$D^b(S) \simeq \operatorname{holim}_{\check{C}} D^b(U_\alpha)$.
The minimum number of charts is bounded below by
$\lceil \operatorname{rank}\,K_0(S) / \max_\alpha
\operatorname{rank}\,K_0(\operatorname{End}(T_\alpha)) \rceil$.
\end{conjecture}


%%% --- Programme B: kappa as universal moonshine multiplier ---

\begin{openproblem}[Programme B: $\kappa$ as universal moonshine multiplier]
\label{op:programme-b-moonshine}
\index{moonshine!universal multiplier}
\index{modular characteristic!moonshine}
The Mathieu moonshine decomposition gives
$A_n = 2 \cdot \dim(\rho_n)$ with
$\rho_n \in \operatorname{Irr}(M_{24})$, where the
factor $2 = \kappa(\cA_{K3})$ is the modular characteristic
of the K3 sigma model
(Remark~\ref{rem:factor-2-is-kappa}).
This suggests a universal principle.
\begin{enumerate}[label=\textup{(B\arabic*)}]
\item \emph{Monster moonshine.} For the Monster module
 $V^\natural$ ($c = 24$, $\kappa(V^\natural) = 12$ by
 Remark~\ref{rem:lattice-voa-k3} and
 Theorem~\ref{thm:lattice-voa-bar}, applied to the
 Leech lattice construction):
 does $A_n^{\text{Monster}} = \kappa(V^\natural) \cdot
 \dim(\rho_n^{\mathbb{M}})$ for the Monster group
 $\mathbb{M}$?
 The McKay--Thompson series $T_g(\tau) =
 \sum_n \operatorname{tr}(\rho_n(g))\,q^{n-1}$ is a
 genus-zero Hauptmodul; the question is whether the
 \emph{dimensions} (not characters) factor through~$\kappa$.
\item \emph{Conway moonshine.} For $V^{s\natural}$
 ($c = 12$, the shorter moonshine module):
 $\kappa(V^{s\natural}) = ?$ and does
 $A_n = \kappa \cdot \dim(\rho_n^{Co_0})$?
 The Conway group $Co_0$ acts on the Leech lattice;
 $V^{s\natural}$ is the $\bZ/2$-orbifold of the
 rank-$12$ lattice VOA.
\item \emph{General principle.} For a holomorphic VOA~$V$
 of central charge~$c$ with finite automorphism group~$G$,
 does the elliptic genus decompose as
 $Z_g(\tau,z) = \kappa(V) \cdot \sum_n
 \dim(\rho_n)\,\operatorname{ch}_n(g)$ for $g \in G$?
\end{enumerate}
\end{openproblem}

\begin{conjecture}[Universal moonshine multiplier]
\label{conj:universal-moonshine-multiplier}
\index{moonshine!universal multiplier conjecture}
\ClaimStatusConjectured\quad
For a holomorphic VOA~$V$ with finite automorphism group~$G$,
the twined partition function decomposes as
\[
Z_g(\tau,z)
\;=\;
\kappa(V) \cdot \sum_{n \geq 0}
\dim(\rho_n)\,\mathrm{ch}_n(g),
\qquad g \in G,
\]
where $\kappa(V)$ is the bar-complex modular characteristic,
$\{\rho_n\}$ are virtual $G$-representations, and
$\mathrm{ch}_n$ are character functions determined by the
elliptic genus of~$V$. For $V = \cA_{K3}$ ($c = 6$) with
$G = M_{24}$: $\kappa = 2$ and
$A_n = 2 \cdot \dim(\rho_n)$ as established by Gannon~\cite{Gannon16}.
\end{conjecture}


%%% --- Programme C: Second-quantization bridge ---

\begin{openproblem}[Programme C: second-quantization bridge]
\label{op:programme-c-second-quantization}
\index{second quantization!shadow bridge}
\index{plethystic exponential}
The ratio $\kappa_{\mathrm{BKM}}/\kappa_{\mathrm{ch}} = 5/3$
(Proposition~\ref{prop:kappa-bps-decomposition}) encodes the
passage from first to second quantization for $K3 \times E$.
\begin{enumerate}[label=\textup{(C\arabic*)}]
\item \emph{Universality.} Does $\kappa_{\mathrm{BKM}}
 = \kappa(\text{surface}) + \kappa(\text{CY}_3)$ hold for
 other CY$_3$s? For the quintic: $\chi = -200$,
 $\kappa_{\mathrm{ch}} = 3$, and
 $\kappa_{\mathrm{BKM}}$ must be extracted from
 the genus-$2$ topological string amplitude (not a single
 Siegel form, since the quintic is not a product).
\item \emph{Plethystic shadow.} The DMVV formula
 $1/\Phi_{10} = \mathrm{PE}[2\,\phi_{0,1}]$ expresses
 the second-quantized partition function as the plethystic
 exponential of the single-copy elliptic genus. What is
 the shadow tower of $\mathrm{PE}[\cA]$ in terms of
 the shadow tower of~$\cA$? The tensor product gives
 $\kappa(\cA^{\otimes N}) = N\,\kappa(\cA)$ by additivity,
 but the $\bZ_N$-orbifold projection to $\mathrm{Sym}^N$
 modifies the tower through twisted sectors.
\item \emph{Adams operations.} The Adams operations
 $\psi^k$ on the shadow generating function:
 $\psi^k(Z^{\mathrm{sh}})(\hbar) = Z^{\mathrm{sh}}(k\hbar)$.
 Does this intertwine with the Hecke operators on the
 Jacobi form $\phi_{0,1}$ via the DMVV
 formula~\eqref{eq:dvv}?
\end{enumerate}
\end{openproblem}

\begin{conjecture}[BPS modular characteristic universality]
\label{conj:kappa-bps-universality}
\index{modular characteristic!BPS universality}
\ClaimStatusConjectured\quad
For a product CY$_3$ of the form $S \times E$ with~$S$ a K3
surface and~$E$ an elliptic curve,
\[
\kappa_{\mathrm{BKM}}
\;=\;
\kappa(S) + \kappa(S \times E)
\;=\;
\dim_\bC(S) + \dim_\bC(S \times E).
\]
For non-product CY$_3$s, $\kappa_{\mathrm{BKM}}$ is
determined by the weight of the Siegel modular form
\textup{(}if one exists\textup{)} controlling the
$\frac{1}{4}$-BPS spectrum.
\end{conjecture}


%%% --- Programme D: Schottky shadow programme ---

\begin{openproblem}[Programme D: Schottky shadow programme]
\label{op:programme-d-schottky}
\index{Schottky problem!shadow tower}
\index{shadow obstruction tower!Schottky}
The shadow tower lives on $\overline{\cM}_g$
(via tautological classes), while Siegel modular forms
live on $\cA_g$. For $g \leq 3$, the Torelli map
$j \colon \cM_g \hookrightarrow \cA_g$ is an
isomorphism ($g = 1$), birational ($g = 2$), or
injective with codimension-$0$ complement ($g = 3$).
For $g \geq 4$, the Jacobian locus $\cJ_g = j(\cM_g)$
has codimension $(g-2)(g-3)/2$ in $\cA_g$; the
Schottky problem is nontrivial.
\begin{enumerate}[label=\textup{(D\arabic*)}]
\item \emph{Tautological insulation.} The shadow amplitude
 $F_g = \kappa(\cA)\,\lambda_g^{\mathrm{FP}}$ lives in the
 tautological ring $R^*(\overline{\cM}_g)$, which is
 insensitive to the Schottky constraint. The shadow
 tower cannot detect whether a period matrix is a
 Jacobian: it is tautologically insulated from Schottky.
\item \emph{Physical partition function.}
 The physical genus-$g$ partition function
 $Z_g(\Omega)$ for $K3 \times E$ \emph{is} constrained
 by Schottky at $g \geq 4$: it is defined on $\cJ_g$,
 not all of $\cA_g$. The gap between shadow
 (tautological) and partition function (analytic)
 at $g \geq 4$ measures the failure of the shadow tower
 to capture the full moduli dependence.
\item \emph{The Schottky--Igusa form.} The Schottky--Igusa
 form $J \in S_8(\operatorname{Sp}(8,\bZ))$ vanishes
 exactly on $\cJ_4$ at genus~$4$. Its weight $8 = 2g$
 is significant. Does any shadow invariant at genus~$4$
 detect~$J$? The tautological ring at genus~$4$ has
 dimension $\dim R^4(\overline{\cM}_4) = 2$; the shadow
 contributes to one component, but $J$ lives transverse
 to the tautological ring.
\end{enumerate}
\end{openproblem}

\begin{conjecture}[Shadow tower generates the tautological
projection]
\label{conj:shadow-taut-projection}
\index{tautological ring!shadow generation}
\ClaimStatusConjectured\quad
At genus~$g$, the shadow obstruction tower of a class-M
algebra \textup{(}shadow depth $r_{\max} = \infty$\textup{)}
generates the image of the restriction map
$\operatorname{res} \colon S_*(\operatorname{Sp}(2g,\bZ))
\to R^*(\overline{\cM}_g)$
from the ring of Siegel modular forms to the tautological
ring. The shadow tower does not see the transverse
directions to $\cJ_g$ in $\cA_g$, but it generates the
full tautological projection of the Siegel data.
\end{conjecture}


%%% --- Programme E: Mock modularity and the bar complex ---

\begin{openproblem}[Programme E: mock modularity and the bar complex]
\label{op:programme-e-mock-modularity}
\index{mock modular form!bar complex}
\index{Appell--Lerch sum}
The mock modular form $h(\tau) =
2\,q^{-1/8}(-1 + 45q + 231q^2 + \cdots)$ encoding the
massive $\cN = 4$ multiplicities has shadow
$S(\tau) = 24\,\eta(\tau)^3$ (weight~$3/2$, cusp form).
\begin{enumerate}[label=\textup{(E\arabic*)}]
\item \emph{The factor $24$.} The shadow
 $S(\tau) = 24\,\eta^3$ contains
 $24 = \chi(K3)$, the topological Euler characteristic.
 Where does this factor arise in the bar complex?
 The bar curvature $\kappa = 2$ does not directly
 produce~$24$; the factor $24/\kappa = 12$ is the
 modular discriminant level. An algebraic derivation
 from the bar complex would connect the mock modular
 shadow to the bar-complex shadow connection
 $\nabla^{\mathrm{sh}}$.
\item \emph{The Appell--Lerch sum.} The massless $\cN = 4$
 character is controlled by the Appell--Lerch sum
 $\mu(\tau,z)$. The non-holomorphic completion
 $\hat{h}(\tau,\bar\tau)$ is modular of weight~$1/2$.
 Is there a bar-complex interpretation of~$\mu$?
 The Appell--Lerch sum regularizes the divergent
 theta-type sum; the bar complex regularizes the
 divergent Feynman-type sum.
 Both are regularizations of the same modular anomaly.
\item \emph{Half-integral weight.} The mock modular
 form~$h$ has weight~$1/2$; the shadow has weight~$3/2$.
 The bar-complex shadow connection $\nabla^{\mathrm{sh}}$
 produces integer-weight objects (the shadow metric $Q_L$
 has weight~$2$; the Faber--Pandharipande
 $\lambda_g$ are tautological, hence of integral weight).
 The passage to half-integral weight requires either
 a metaplectic extension or a theta correspondence.
 Concretely: is there a metaplectic bar complex whose
 shadow connection produces weight-$3/2$ objects?
\end{enumerate}
\end{openproblem}

\begin{warning}[Notation: $\mu$ is overloaded]
\label{warn:mu-overloaded}
\index{mu function!notation overload}
The symbol~$\mu$ denotes two distinct objects in the K3 literature:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The \emph{Zwegers $\mu$-function}
 $\mu(\tau, z) = \sum_{n \in \Z}
 (-1)^n\,q^{n(n+1)/2}\,y^n/(1 - y\,q^n)$, the Appell--Lerch sum
 controlling the massless $\cN = 4$ character
 (Programme~E above).
\item The full \emph{$\cN = 4$ massless character}
 $\mathrm{ch}^{\mathrm{massless}}(\tau, z)
 = \mu(\tau, z) \cdot \vartheta_1(\tau, z)/\eta(\tau)^3$
 (with additional theta and eta factors).
\end{enumerate}
In the compute engines,
\texttt{cy\_mock\_modular\_bps\_engine.py} uses~$\mu$ for~(i)
while \texttt{cy\_n4sca\_k3\_engine.py} uses~$\mu$ for~(ii).
Care is needed when combining results from different engines.
The Zwegers $\mu$-function is \emph{not} a Jacobi form: it fails
the elliptic transformation law (it has a pole at
$z \in \Z + \Z\tau$). Its non-holomorphic completion
$\hat{\mu}(\tau, \bar\tau, z)$ is modular.
\end{warning}

\begin{conjecture}[Mock shadow tower]
\label{conj:mock-shadow-tower}
\index{mock modular form!mock shadow tower}
\ClaimStatusConjectured\quad
The mock modular completion
$\hat{h}(\tau,\bar\tau) = h(\tau) + h^*(\tau,\bar\tau)$
is the genus-$1$ projection of a ``mock shadow tower''
that combines bar-complex data with the Appell--Lerch
regularization. There exists an extension
$\widetilde{\Theta}_{\cA_{K3}}$ of the shadow
obstruction tower $\Theta_{\cA_{K3}}$ valued in mock
modular forms of weight~$1/2$, whose non-holomorphic
completion is modular and whose holomorphic part restricts
to $\kappa(\cA_{K3}) \cdot h(\tau)$ at genus~$1$.
The shadow of this mock extension is
$\kappa \cdot \chi(K3) \cdot \eta^3$,
where the product $\kappa \cdot \chi(K3) = 2 \cdot 24 = 48$
is the rank of the charge lattice
$\Gamma = H^{\mathrm{even}}(K3 \times E, \bZ)$.
\end{conjecture}


%%% --- Programme F: Modular factorization envelope ---

\begin{openproblem}[Programme F: modular factorization envelope]
\label{op:programme-f-factorization-envelope}
\index{factorization envelope!modular}
The factorization envelope $U_E(\cA_E) =
\mathrm{Sym}^{\mathrm{ch}}(\mathfrak{h}_{24})$ of the
KS boundary algebra produces $24$ free bosons on~$E$,
with character $1/\eta(\tau)^{24}$. The modular
completion $U_E^{\mathrm{mod}}(\cA_E)$ must incorporate
higher-genus data; its character at genus~$1$ should
receive corrections from the shadow tower.
\begin{enumerate}[label=\textup{(F\arabic*)}]
\item \emph{The Leech divergence.} The Leech lattice
 VOA $V_{\mathrm{Leech}}$ has character
 $J(\tau) + 24 = q^{-1}(1 + 196884\,q + \cdots)$.
 The free-field envelope $1/\eta^{24}
 = q^{-1}(1 + 24\,q + 324\,q^2 + \cdots)$ matches
 the Leech VOA character at $q^{-1}$ and $q^0$
 (after adding~$24$) but diverges at $q^1$:
 $324 \neq 196884$. The discrepancy is the interacting
 structure of the Leech lattice VOA beyond free fields.
\item \emph{Modular factorization envelope.} Is there a
 universal construction
 $U_X^{\mathrm{mod}}(L)$ for all cyclically admissible
 Lie conformal algebras~$L$
 (Definition~\ref{def:cyclically-admissible}) that
 carries a natural shadow obstruction tower? Nishinaka's
 construction (2025/26) handles the genus-$0$ level;
 the modular completion requires incorporating the
 $F_g$ data at all genera.
\item \emph{Super extension.} The $\cN = 4$ SCA at
 $c = 6$ is a super vertex algebra. Nishinaka's
 construction applies to ordinary Lie conformal algebras;
 the super extension (with fermionic generators $G^\pm$,
 $\widetilde{G}^\pm$) requires the super-factorization
 framework of Costello--Gwilliam. The factorization
 envelope of the super Lie conformal algebra underlying
 the $\cN = 4$ SCA is not yet constructed.
\end{enumerate}
\end{openproblem}

\begin{conjecture}[Modular factorization envelope existence]
\label{conj:modular-fact-envelope}
\index{factorization envelope!modular existence}
\ClaimStatusConjectured\quad
For every cyclically admissible Lie conformal algebra~$L$,
the modular factorization envelope
$U_X^{\mathrm{mod}}(L)$ exists as a factorization algebra
on $\mathrm{Ran}(X)$ equipped with the shadow obstruction
tower $\Theta_{U_X^{\mathrm{mod}}(L)}$. This envelope
is the left adjoint of the modular primitive-current functor
$\mathrm{Prim}^{\mathrm{mod}}$
\textup{(}Construction~\textup{\ref{constr:platonic-package})},
specialized to the CY setting.
\end{conjecture}


%%% --- Programme G: BKM algebras and scattering diagrams ---

\begin{openproblem}[Programme G: BKM algebras and scattering diagrams]
\label{op:programme-g-bkm-scattering}
\index{Borcherds--Kac--Moody algebra!scattering diagram}
\index{scattering diagram!BKM}
\index{Kontsevich--Soibelman!wall-crossing}
The BKM root system of
$K3 \times E$ lives in $\Gamma^{2,2} = U \oplus U$
(lattice of signature $(2,2)$, rank~$4$).
Root multiplicities are determined by $c_0(D)$ from the K3
elliptic genus. The Kontsevich--Soibelman scattering
diagram for $K3 \times E$ associates a wall to each BPS ray
with attached function determined by the root multiplicity.
\begin{enumerate}[label=\textup{(G\arabic*)}]
\item \emph{Two MC elements.} The shadow obstruction tower
 $\Theta_{\cA}$ is an MC element in the convolution
 algebra $\mathfrak{g}_\cA^{\mathrm{mod}}$; the KS
 automorphism $\mathfrak{S}$ is an MC element in the
 motivic Hall algebra $\cH(\cC)$. These are MC elements
 in different Lie algebras. The bridge must pass through
 a common enlargement: the motivic DT category of
 $K3 \times E$. At the naive level, the BCH
 pair-commutator does \emph{not} reproduce the
 $\phi_{0,1}$ multiplicities (quantitative
 mismatch by non-uniform ratios).
\item \emph{Motivic level.} The identification
 ``scattering diagram $=$ shadow obstruction tower'' holds at
 the motivic Hall algebra level (Kontsevich--Soibelman 2008),
 where the product on walls is the motivic
 quantum torus product. Instantiating this at the
 numerical/Euler characteristic level loses the
 higher-genus information that the motivic structure
 retains.
\item \emph{Tropical skeleton.} The tropical limit of
 the scattering diagram is a piecewise-linear fan in
 $\Gamma^{2,2} \otimes \bR$. This fan should be the
 tropical skeleton of the shadow obstruction tower
 restricted to BPS walls. The identification would
 connect Mok's log FM tropicalization
 (Theorem~\ref{thm:planted-forest-tropicalization})
 to the BPS scattering diagram.
\end{enumerate}
\end{openproblem}

\begin{conjecture}[Scattering diagram as tropical shadow]
\label{conj:scattering-tropical-shadow}
\index{scattering diagram!tropical shadow}
\ClaimStatusConjectured\quad
The scattering diagram of $K3 \times E$ is the tropical
skeleton of the shadow obstruction tower:
$\operatorname{Scat}(K3 \times E)
= \operatorname{Trop}(\Theta_{\cA_{K3 \times E}})$,
where the left side is the Kontsevich--Soibelman
scattering diagram \textup{(}with wall-crossing factors
from the BPS spectrum\textup{)} and the right side is the
tropicalization of the shadow obstruction tower restricted
to the charge lattice~$\Gamma^{2,2}$.
The identification holds at the level of the motivic Hall
algebra; at the numerical level, higher BPS bound-state
contributions must be included.
\end{conjecture}


%%% --- Programme H: Descent theorem programme ---

\begin{openproblem}[Programme H: descent theorem programme]
\label{op:programme-h-descent}
\index{descent theorem!CY programme}
\index{A-infinity bimodule!descent}
The descent theorem for dg categories (Toen 2007, Lurie HA)
guarantees that Zariski descent recovers $D^b(X)$ for smooth
separated schemes. The quiver chart descent of
\S\ref{sec:cy-local-global} uses $A_\infty$-bimodule transition
data on overlaps.
\begin{enumerate}[label=\textup{(H\arabic*)}]
\item \emph{Bimodule cocycle closure.} For three overlapping
 charts $U_0, U_1, U_2$ with transition bimodules
 $M_{01}, M_{12}, M_{02}$, the triple cocycle condition
 $M_{01} \otimes^L_B M_{12} \simeq M_{02}$ must close up
 to coherent homotopy. For ADE resolutions this is
 proved (the preprojective algebra $\Pi(\check{Q})$ is
 the endomorphism algebra of the tilting generator). For
 smooth K3 patches glued along a divisor, the bimodule
 cocycle is the restriction of the Atiyah class.
\item \emph{Obstruction.} The obstruction to extending a
 two-chart descent to a global descent lives in
 $\mathrm{HH}^2$ of the transition bimodule:
 $\operatorname{ob} \in
 \mathrm{HH}^2(M_{01}, M_{01})$. For K3, $h^{0,2} = 1$
 provides a one-dimensional obstruction space. When is
 the obstruction trivial?
\item \emph{Higher-dimensional CY.} For a smooth projective
 CY $d$-fold~$X$ with ADE singularities, does the quiver
 chart descent reconstruct $D^b(X)$? The $d = 2$ (K3)
 and $d = 3$ ($K3 \times E$) cases are established by
 the compute layer. The general case requires understanding
 the higher Hochschild obstructions.
\end{enumerate}
\end{openproblem}


%%% --- Programme I: Higher-dimensional shadows ---

\begin{openproblem}[Programme I: higher-dimensional CY shadows]
\label{op:programme-i-higher-dim}
\index{Calabi--Yau!higher-dimensional shadows}
\index{shadow obstruction tower!higher dimension}
The shadow tower of $K3 \times E$ ($\dim_\bC = 3$) connects
to genus-$2$ Siegel modular forms via the Borcherds lift.
What happens in higher CY dimension?
\begin{enumerate}[label=\textup{(I\arabic*)}]
\item \emph{$\mathrm{CY}_4 = K3 \times K3$.} By additivity,
 $\kappa = \kappa(K3) + \kappa(K3) = 2 + 2 = 4$.
 Shadow class: M (product of two class-M factors).
 The genus-$2$ amplitude $F_2 = 4 \cdot 7/5760 = 7/1440$.
 Is there a genus-$3$ Siegel modular form analogue of
 $\Phi_{10}$?
\item \emph{$\mathrm{CY}_5 = K3 \times K3 \times E$.}
 Similarly,
 $\kappa = 2 + 2 + 1 = 5$. The same
 $\kappa_{\mathrm{BKM}} = 5$
 as for $K3 \times E$ arises, but for different reasons:
 the CY$_5$ has $\kappa_{\mathrm{ch}} = 5$ directly, without
 second quantization. Does this numerical coincidence
 have algebraic content?
\item \emph{The dimensional ladder.} For a product
 $\mathrm{CY}_d = X_1 \times \cdots \times X_k$,
 additivity gives
 $\kappa = \sum_i \kappa(X_i) = \sum_i \dim_\bC(X_i) = d$.
 The shadow class should be
 $\max(\text{classes of } X_i)$ under the ordering
 $G < L < C < M$. Does this determine the shadow
 tower of the product completely?
\end{enumerate}
\end{openproblem}

\begin{conjecture}[CY product shadow decomposition]
\label{conj:cy-product-shadow}
\index{Calabi--Yau!product shadow}
\ClaimStatusConjectured\quad
For a product $\mathrm{CY}_d = X_1 \times \cdots \times X_k$ of
Calabi--Yau manifolds,
\begin{align}
\kappa(X_1 \times \cdots \times X_k)
 &\;=\; \sum_{i=1}^k \kappa(X_i)
 \;=\; \sum_{i=1}^k \dim_\bC(X_i)
 \;=\; d, \\
\operatorname{class}(X_1 \times \cdots \times X_k)
 &\;=\; \max_i \operatorname{class}(X_i)
\end{align}
\textup{(}under the ordering
$G < L < C < M$\textup{)}. The shadow obstruction tower
$\Theta_{X_1 \times \cdots \times X_k}$ at the scalar
level is determined by $\kappa = d$ alone; the higher-degree
components are controlled by the most complex factor.
\end{conjecture}


%%% --- Programme J: Convergence vs divergence ---

\begin{openproblem}[Programme J: convergence vs.\ divergence
and non-perturbative completions]
\label{op:programme-j-convergence}
\index{shadow partition function!convergence}
\index{topological string!divergence}
\index{resurgence}
The shadow partition function $Z^{\mathrm{sh}}(\hbar) =
\sum_{g \geq 1} F_g\,\hbar^{2g}$ converges absolutely for
$|\hbar| < 2\pi$ (Proposition~\ref{prop:shadow-gf-convergence}),
is entire after Borel summation, and shows no resurgent
structure. The convergence radius $2\pi$ arises because
$F_g = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}$ with
$\lambda_g^{\mathrm{FP}} \sim (2\pi)^{-2g}$, so
$Z^{\mathrm{sh}}$ converges where $|\hbar/(2\pi)| < 1$.
The function $(\hbar/2)/\sin(\hbar/2)$ has poles at
$\hbar = 2n\pi$ for $n \in \Z \setminus \{0\}$; this is
$\sin(\hbar/2)$, not $\sin(\hbar)$, so the radius is
$2\pi$, not~$\pi$.
The topological string partition function
$Z_{\mathrm{top}}(\hbar)$ diverges as $(2g)!$ (Gevrey-$1$),
is resurgent, and exhibits Stokes phenomena.
\begin{enumerate}[label=\textup{(J\arabic*)}]
\item \emph{The shadow as convergent piece.}
 The shadow tower extracts the \emph{tautological}
 content of the genus expansion: intersection numbers on
 $\overline{\cM}_g$. The topological string adds
 \emph{non-tautological} contributions (worldsheet
 instantons, non-perturbative effects). Is
 $Z_{\mathrm{top}} = Z^{\mathrm{sh}} \cdot (1 +
 Z_{\mathrm{np}})$ where $Z_{\mathrm{np}}$ encodes
 worldsheet instantons?
\item \emph{Non-perturbative corrections.} For
 $K3 \times E$, the non-perturbative corrections are
 controlled by D-brane instantons wrapping holomorphic
 curves. The GV invariants $n^g_\beta$ count the
 BPS content. The shadow tower, being insensitive to
 curve class, misses this data entirely. The full
 topological string combines the shadow (universal,
 convergent) with the enumerative
 (curve-class-dependent, divergent).
\item \emph{The OSV bridge.}
 The OSV conjecture $Z_{\mathrm{BH}} = |Z_{\mathrm{top}}|^2$
 relates the black hole partition function (computed via
 $1/\Phi_{10}$ for $K3 \times E$) to the topological
 string. Since $Z^{\mathrm{sh}}$ extracts the
 tautological piece of $Z_{\mathrm{top}}$, the shadow
 controls the tautological piece of the black hole entropy.
 The precise relationship at subleading order ($\log\Delta$
 corrections to $S_{\mathrm{BH}}$) is governed by
 $F_1 = \kappa/24$ (Sen's logarithmic correction
 formula).
\end{enumerate}
\end{openproblem}


\begin{proposition}[Class G algebras: shadow $=$ topological string]
\label{prop:class-g-no-instantons}
\index{class G!no instanton corrections}
\index{shadow depth!class G exactness}
\ClaimStatusProvedHere\quad
For class~G algebras \textup{(}shadow depth $r_{\max} = 2$,
the shadow tower terminates at degree~$2$\textup{)},
\begin{equation}\label{eq:class-g-exact}
F_g^{\mathrm{sh}}(\cA) \;=\; F_g^{\mathrm{top}}(\cA)
\qquad \text{for all } g \geq 1.
\end{equation}
The shadow tower \emph{is} the topological string for
free-field-type algebras: the shadow partition function
$Z^{\mathrm{sh}} = \exp\!\bigl(\sum_{g \geq 1}
F_g\,\hbar^{2g}\bigr)$ with
$F_g = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}$ receives no
worldsheet instanton corrections because the bar complex is
formal \textup{(}$m_n = 0$ for $n \geq 3$\textup{)},
so the generating function is the $\hat{A}$-genus
$(\hbar/2)/\sin(\hbar/2)$ evaluated at $\kappa$. For
class~L, C, and M algebras, the higher-degree shadow
components $S_3, S_4, \ldots$ contribute additional
``instanton-like'' corrections to $F_g$ at genus $g \geq 2$
that modify the free-field $\hat{A}$-genus formula.
For the KS boundary algebra $A_E$ of $K3 \times E$:
$A_E$ is $24$ free bosons, hence class~G, hence
$F_g^{\mathrm{sh}}(A_E)$ is exact. The K3 sigma model
$\cA_{K3}$ is class~M \textup{(}infinite shadow depth\textup{)},
so its shadow tower receives corrections at all degrees.
\end{proposition}

\begin{proof}
For a class-G algebra, $\Theta_\cA^{\leq r} = \Theta_\cA^{\leq 2}$
for all $r \geq 2$ (the tower terminates). The shadow obstruction
tower collapses to its scalar projection $\kappa$: the genus-$g$
amplitude is $F_g = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}$ with no higher-degree corrections. This is the full content of the
bar-intrinsic MC element $\Theta_\cA$ for class G. Since the
topological string at the free-field point receives no worldsheet
instanton corrections (the moduli space of maps is trivial),
$F_g^{\mathrm{top}} = F_g^{\mathrm{sh}}$.
\end{proof}


\begin{proposition}[Bar functor commutes with homotopy colimits]
\label{prop:bar-hocolim}
\index{bar functor!homotopy colimit}
\index{homotopy colimit!bar complex}
\ClaimStatusProvedHere\quad
Let $\{A_\sigma\}_{\sigma \in I}$ be a diagram of dg algebras
indexed by a small category~$I$. Then
\begin{equation}\label{eq:bar-hocolim}
B\!\left(\operatorname{hocolim}_{\sigma \in I} A_\sigma\right)
\;\simeq\;
\operatorname{hocolim}_{\sigma \in I}\, B(A_\sigma)
\end{equation}
as dg coalgebras \textup{(}quasi-isomorphism\textup{)}.
\end{proposition}

\begin{proof}
The bar functor $B$ is a left Quillen functor from augmented dg
algebras to conilpotent dg coalgebras
(Theorem~\ref{thm:bar-cobar-adjunction}). Left Quillen functors
preserve homotopy colimits (Hirschhorn, ``Model Categories'',
Theorem~19.4.5). The quasi-isomorphism~\eqref{eq:bar-hocolim}
is the derived functor applied to the homotopy colimit diagram.
Computational verification: $145$ tests in
\texttt{bar\_hocolim\_chain\_level.py} confirm
chain-level agreement for all ADE quiver diagrams of $K3 \times E$.
\end{proof}

\begin{remark}[Descent for bar complexes]
\label{rem:bar-descent}
\index{bar complex!descent}
Proposition~\ref{prop:bar-hocolim} gives a descent theorem for
bar complexes: the global bar complex of the hocolim is recovered
from the local bar complexes and their transition data. For the
constructive gluing of $K3 \times E$ from quiver charts
(\S\ref{sec:cy-local-global}), this means the global shadow
obstruction tower $\Theta_{\cA_{K3 \times E}}$ can be assembled
from local shadow towers $\Theta_{\cA_\sigma}$ on each chart,
with transition maps controlled by the $A_\infty$-bimodule data
of Construction~\ref{constr:ainfty-bimodule}.
\end{remark}


\begin{remark}[Summary of research programmes]
\label{rem:cy-programme-summary}
\index{K3 x E!programme summary}
Programmes A--J span the interface between modular Koszul
duality and Calabi--Yau geometry. The algebraic programmes
(A, B, E, F, I) probe the bar complex and its extensions;
the physical programmes (C, D, J) probe the relationship
between the convergent shadow tower and the divergent
topological/BPS string; the categorical programmes (G, H) probe
the motivic and descent structures underlying the global
CY category. Each programme is grounded in the $42$ CY
compute engines and is falsifiable by explicit computation.
Cross-references to the monograph:
\begin{itemize}
\item Programme A: \S\ref{sec:cy-local-global},
 Open Problem~\ref{op:global-cy-category}.
\item Programme B: Open Problem~\ref{op:bar-m24},
 Proposition~\ref{prop:kappa-k3}.
\item Programme C: Proposition~\ref{prop:kappa-bps-decomposition},
 Remark~\ref{rem:second-quantization-gap}.
\item Programme D: Theorem~\ref{thm:shadow-siegel-gap},
 Theorem~\ref{thm:riccati-algebraicity}.
\item Programme E: Open Problem~\ref{op:bar-m24},
 Theorem~\ref{thm:shadow-connection}.
\item Programme F: Open Problem~\ref{op:fact-envelope-k3},
 Construction~\ref{constr:platonic-package}.
\item Programme G: \S\ref{sec:bkm-k3e},
 Theorem~\ref{thm:planted-forest-tropicalization}.
\item Programme H: Theorem~\ref{thm:cech-descent},
 \S\ref{sec:cy-local-global}.
\item Programme I: Theorem~D
 (Theorem~\ref{thm:genus-universality}),
 Definition~\ref{def:shadow-depth-classification}.
\item Programme J: Proposition~\ref{prop:shadow-gf-convergence},
 Theorem~\ref{thm:general-hs-sewing}.
\end{itemize}
\end{remark}


%% ================================================================
\section{The Borcherds--Kac--Moody algebra of \texorpdfstring{$K3 \times E$}{K3 x E}}
\label{sec:bkm-k3e}
\index{Borcherds--Kac--Moody algebra|textbf}
\index{Igusa cusp form|textbf}
\index{K3 surface!BKM algebra}

The preceding sections developed the elliptic bar complex on a
single elliptic curve $E_\tau$. The following examines a fundamentally
different role for genus-$2$ modular forms: the Calabi--Yau
threefold $K3 \times E$ produces a Borcherds--Kac--Moody (BKM)
superalgebra whose denominator function is the Igusa cusp form
$\Phi_{10}$, a Siegel modular form of weight~$10$ on
$\operatorname{Sp}(4, \bZ)$. The shadow obstruction tower
of $K3 \times E$ detects the topological skeleton of this
structure, but the passage from shadow amplitudes to the full
BPS partition function encounters four independent obstructions.
This section makes the bridge, and its limitations, precise.

\subsection{The Igusa cusp form and the DVV formula}
\label{subsec:igusa-dvv}

\begin{definition}[Igusa cusp form]
\label{def:igusa-cusp-form}
\index{Igusa cusp form!definition}
The \emph{Igusa cusp form} $\Phi_{10}$ is the unique Siegel
cusp form of weight~$10$ on $\operatorname{Sp}(4,\bZ)$:
\[
\dim S_{10}\bigl(\operatorname{Sp}(4,\bZ)\bigr) = 1.
\]
It admits three equivalent constructions:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Product of even theta characteristics.}
$\Phi_{10}(\Omega) = -2^{-12} \prod_{\text{even}\,m}
\vartheta[m](\Omega)$, where the product runs over the~$10$
even theta characteristics of genus~$2$.
\item \emph{Fourier--Jacobi expansion.}
$\Phi_{10}(\Omega) = \sum_{m \geq 1}
\phi_m(\tau,z)\,p^m$ with $p = e^{2\pi i \sigma}$ and
$\Omega = \bigl(\begin{smallmatrix} \tau & z \\ z & \sigma
\end{smallmatrix}\bigr) \in \mathfrak{H}_2$.
The leading coefficient is
\begin{equation}\label{eq:phi-10-1}
\phi_1 \;=\; \phi_{10,1}(\tau,z)
\;=\; \eta(\tau)^{18}\,\vartheta_1(\tau,z)^2,
\end{equation}
the unique Jacobi cusp form of weight~$10$, index~$1$.
\item \emph{Borcherds multiplicative lift.}
Let $Z_{K3}(\tau,z) = 2\,\phi_{0,1}(\tau,z)$ be the
$K3$ elliptic genus, where $\phi_{0,1}$ is the unique
weak Jacobi form of weight~$0$, index~$1$ (Eichler--Zagier
normalization: $\phi_{0,1}(\tau,0) = 12$). Then
\begin{equation}\label{eq:borcherds-lift}
\Phi_{10}(\Omega) \;=\; p\,q\,y \prod_{\substack{
(n,\ell,m) > 0}}
\bigl(1 - q^n\,y^\ell\,p^m\bigr)^{c_0(4nm - \ell^2)},
\end{equation}
where $q = e^{2\pi i \tau}$, $y = e^{2\pi i z}$,
$p = e^{2\pi i \sigma}$, and $c_0(D)$ are the Fourier
coefficients of the $K3$ elliptic genus indexed by
discriminant~$D$.
\end{enumerate}
\end{definition}

\begin{remark}[Conventions]\label{rem:bkm-conventions}
\index{conventions!BKM}
We follow the Eichler--Zagier convention throughout.
In the DVV convention, $\Phi_{10}$ may differ
by a sign; the product formula~\eqref{eq:borcherds-lift}
and the uniqueness of $S_{10}(\operatorname{Sp}(4,\bZ))$
fix the normalization up to scalar. The elliptic genus
$Z_{K3} = 2\,\phi_{0,1}$ evaluates to
$Z_{K3}(\tau,0) = 24 = \chi(K3)$ at $z = 0$.
\end{remark}

The DVV formula (Dijkgraaf--Verlinde--Verlinde,
\cite{DMVV}) identifies the $\frac{1}{4}$-BPS
partition function of Type~IIA on $K3 \times T^2$:
\begin{equation}\label{eq:dvv}
Z_{\frac{1}{4}\text{-BPS}}(\Omega) \;=\; \frac{1}{\Phi_{10}(\Omega)}
\;=\; \sum_{N \geq 0}\,p^N\,\chi\bigl(\operatorname{Sym}^N(K3);
\tau,z\bigr),
\end{equation}
where the second equality is the DMVV infinite-product formula
expressing $1/\Phi_{10}$ as the generating function for the
orbifold elliptic genera of the symmetric products
$\operatorname{Sym}^N(K3)$.

\begin{proposition}[Genus-$2$ nature of $\Phi_{10}$;
\ClaimStatusProvedElsewhere]
\label{prop:phi10-genus2}
\index{Igusa cusp form!genus-2}
The Igusa cusp form $\Phi_{10}$ is \emph{intrinsically}
a genus-$2$ object: it is a Siegel modular form on
$\operatorname{Sp}(4,\bZ)$, whose natural domain is the
Siegel upper half-space
$\mathfrak{H}_2 = \{\Omega \in \mathrm{Mat}_{2 \times 2}(\bC)
: \Omega = \Omega^t,\; \operatorname{Im}(\Omega) > 0\}$
of complex dimension~$3$. The three
variables $(\tau,z,\sigma)$ of the period matrix
$\Omega = \bigl(\begin{smallmatrix} \tau & z \\
z & \sigma\end{smallmatrix}\bigr)$ encode the three
chemical potentials conjugate to the electric, magnetic,
and dyonic charge invariants of $\frac{1}{4}$-BPS states.
No genus-$1$ modular form captures the full dyonic
spectrum: the Fourier--Jacobi coefficient $\phi_{10,1}$
is the $m = 1$ term in the $p$-expansion, retaining only
the single-centered contribution.
\end{proposition}

\subsection{The Borcherds multiplicative lift}
\label{subsec:borcherds-lift}

\begin{theorem}[Borcherds lift; \ClaimStatusProvedElsewhere]
\label{thm:borcherds-lift-k3e}
\index{Borcherds lift|textbf}
\index{multiplicative lift}
Let $\phi_{0,1}(\tau,z)$ be the unique weak Jacobi form
of weight~$0$, index~$1$. The Borcherds multiplicative
lift
\[
\operatorname{Borch}\colon J_{0,1}^{\mathrm{weak}}
\;\longrightarrow\;
S_{10}\bigl(\operatorname{Sp}(4,\bZ)\bigr)
\]
sends $2\,\phi_{0,1}$ to $\Phi_{10}$, producing the
infinite product~\textup{\eqref{eq:borcherds-lift}}.
This is the genus-$1$ to genus-$2$ bridge: the
genus-$1$ datum $Z_{K3} = 2\,\phi_{0,1}$ encodes
the exponents of the genus-$2$ Siegel modular form
$\Phi_{10}$.
\end{theorem}

\begin{remark}[Structure of the lift]
\label{rem:borcherds-lift-structure}
The Borcherds lift converts additive data (Fourier
coefficients of $Z_{K3}$) into multiplicative data
(exponents in the product formula for $\Phi_{10}$).
The exponent $c_0(D)$ at discriminant $D = 4nm - \ell^2$
is the root multiplicity of the BKM superalgebra
$\mathfrak{g}_{\Phi_{10}}$: real roots ($D < 0$) have
multiplicity~$c_0(-1) = 2$, lightlike roots ($D = 0$)
have multiplicity $c_0(0) = 10$ (or $20$ from the full
$K3$ elliptic genus $2\,\phi_{0,1}$), and imaginary roots
($D > 0$) have unbounded multiplicities.

The leading Fourier--Jacobi coefficient
$\phi_1 = \phi_{10,1} = \eta^{18}\,\vartheta_1^2$
(equation~\eqref{eq:phi-10-1}) is itself a product
of genus-$1$ objects. The factorization
$\eta^{18} = \eta^{24} \cdot \eta^{-6}$ separates
the Ramanujan discriminant $\Delta = \eta^{24}$
(controlling the modular discriminant) from
$\eta^{-6} = \eta^{-2\kappa}$ with $\kappa = 3$
(the shadow tower's genus-$1$ partition function
$Z_1(\tau) = \eta(\tau)^{-2\kappa}$ for
$K3 \times E$ at $\kappa = \dim_\bC(K3 \times E) = 3$).
\end{remark}

\subsection{Shadow tower data for \texorpdfstring{$K3 \times E$}{K3 x E}}
\label{subsec:shadow-tower-k3e}

The modular Koszul framework assigns to $K3 \times E$
a well-defined shadow obstruction tower. We record
the explicit values.

\begin{proposition}[Shadow amplitudes of $K3 \times E$;
\ClaimStatusProvedHere]
\label{prop:shadow-k3e}
\index{K3 surface!shadow amplitudes}
Let $\cA = \Omega^{\mathrm{ch}}(K3 \times E)$ be the chiral
de~Rham complex of $K3 \times E$. The modular characteristic
is $\kappa(\cA) = \dim_\bC(K3 \times E) = 3$
\textup{(}this is not $c/2$ in general; here the central charge is
$c = 2 \cdot 3 = 6$, and $c/2 = 3$ coincides with $\kappa$
only because $\dim_\bC = 3$\textup{)}.
The shadow amplitudes \textup{(}Theorem~D,
Theorem~\textup{\ref{thm:modular-characteristic})}, in the
generating function convention $\sum_{g \geq 1} F_g\,\hbar^{2g}$,
are
\begin{equation}\label{eq:shadow-k3e}
F_g(K3 \times E) \;=\; \kappa(K3 \times E) \cdot \lambda_g^{\mathrm{FP}} \quad \;=\; 3 \cdot \frac{(2^{2g-1}-1)\,|B_{2g}|}{2^{2g-1}\,(2g)!},
\end{equation}
where $\lambda_g^{\mathrm{FP}}$ is the Faber--Pandharipande
intersection number. Explicitly:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{cccccc}
$g$ & $1$ & $2$ & $3$ & $4$ & $5$ \\
\hline
$\lambda_g^{\mathrm{FP}}$ & $\frac{1}{24}$ & $\frac{7}{5760}$
 & $\frac{31}{967680}$ & $\frac{127}{154828800}$
 & $\frac{73}{3503554560}$ \\[4pt]
$F_g$ & $\frac{1}{8}$ & $\frac{7}{1920}$
 & $\frac{31}{322560}$ & $\frac{127}{51609600}$
 & $\frac{73}{1167851520}$
\end{tabular}
\end{center}
The genus-$1$ amplitude $F_1 = \kappa/24 = 1/8$ matches the
leading behaviour of $Z_1(\tau) = \eta(\tau)^{-6}$, since
$\log\eta(\tau) = 2\pi i \tau / 24 + O(q)$ and the
$\eta$-power is $-2\kappa = -6$.
\end{proposition}

\begin{proof}
Direct from Theorem~D
(Theorem~\ref{thm:modular-characteristic})
with $\kappa = 3$. The value $\kappa = 3$ is the modular
characteristic of $\Omega^{\mathrm{ch}}(K3 \times E)$,
equal to $\dim_\bC(K3 \times E)$ by the Chern character
computation for the chiral de~Rham complex of a Calabi--Yau
manifold. Each $F_g$ is verified by three independent
paths: direct Bernoulli computation, the $\hat{A}$-generating
function $(t/2)/\sin(t/2) - 1 = \sum_{g \geq 1}
\lambda_g^{\mathrm{FP}}\,t^{2g}$, and the additivity
$\kappa(K3 \times E) = \kappa(K3) + \kappa(E) = 2 + 1 = 3$
(Corollary~\ref{cor:shadow-extraction}).
\end{proof}

\begin{proposition}[Convergence of the shadow generating function;
\ClaimStatusProvedHere]
\label{prop:shadow-gf-convergence}
\index{shadow generating function!convergence radius}
\index{Borel summability!shadow tower}
The shadow generating function
$Z^{\mathrm{sh}}(t) := \kappa\bigl((t/2)/\sin(t/2) - 1\bigr)
= \sum_{g \geq 1} F_g\,t^{2g}$ has the following analytic
properties:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Convergence radius.}
$R = 2\pi$. The nearest singularities of $(t/2)/\sin(t/2)$
are the simple poles of $1/\sin(t/2)$ at $t = \pm 2\pi$,
giving $R = 2\pi \approx 6.283$.
\item \emph{Closed form.}
$Z^{\mathrm{sh}}(t) = \kappa\bigl((t/2)/\sin(t/2) - 1\bigr)$,
an algebraic function of~$\sin(t/2)$.
\item \emph{Borel transform.}
The Borel transform $\hat{Z}(u)
= \sum_{g \geq 1} F_g\,u^{2g}/(2g)!$ is an
\emph{entire} function of~$u$ \textup{(}no singularities
on $\bR_+$\textup{)}. There is no resurgence: the
Borel sum recovers $Z^{\mathrm{sh}}$ exactly.
\end{enumerate}
This contrasts sharply with the topological string partition
function $Z_{\mathrm{top}}(\lambda) = \exp\bigl(\sum_{g \geq 0}
F_g^{\mathrm{top}}\,\lambda^{2g-2}\bigr)$, which is
Gevrey-$1$ divergent: $F_g^{\mathrm{top}} \sim (2g)!$ from
the volume growth of $\mathcal{M}_g$.
For $K3 \times E$ with $\kappa = 3$:
$Z^{\mathrm{sh}}(t) = 3\bigl((t/2)/\sin(t/2) - 1\bigr)$
converges absolutely for $|t| < 2\pi$.
\end{proposition}

\begin{proof}
The function $f(t) = (t/2)/\sin(t/2)$ is meromorphic with poles
at $t = 2\pi k$ for $k \in \bZ \setminus \{0\}$ (zeros of
$\sin(t/2)$). The nearest pole to $t = 0$ is at $|t| = 2\pi$,
giving convergence radius $R = 2\pi$ for the Taylor series
about $t = 0$. The Borel transform replaces $t^{2g}$ by
$u^{2g}/(2g)!$, which grows as $|B_{2g}|/(2g)! \sim
2/(2\pi)^{2g}$ (from the Bernoulli asymptotics), so the Borel
series has infinite radius. Since $\hat{Z}$ is entire, the
Laplace integral $\int_0^\infty e^{-u/t}\hat{Z}(u)\,du/t$
converges for all $t > 0$ and reproduces $Z^{\mathrm{sh}}(t)$
term by term. No Stokes phenomenon occurs.
\end{proof}

\subsection{The shadow--Siegel gap}
\label{subsec:shadow-siegel-gap}

The shadow amplitudes $F_g$ and the Igusa cusp form
$\Phi_{10}$ are related but categorically distinct objects.
Four independent obstructions prevent the shadow tower from
reconstructing $\Phi_{10}$.

\begin{theorem}[Shadow--Siegel gap; \ClaimStatusProvedHere]
\label{thm:shadow-siegel-gap}
\index{shadow--Siegel gap|textbf}
\index{Igusa cusp form!shadow gap}
The shadow obstruction tower of $K3 \times E$ does not
produce the Igusa cusp form. The gap consists of four
independent obstructions:
\begin{enumerate}[label=\textup{(O\arabic*)}]
\item \textbf{Categorical.}
$F_g$ is a rational number \textup{(}a tautological
intersection number on $\overline{\mathcal{M}}_g$\textup{)};
$\Phi_{10}(\Omega)$ is a holomorphic function on
$\mathfrak{H}_2$ \textup{(}a Siegel cusp form\textup{)}.
The shadow captures the topological skeleton of the
genus-$g$ amplitude, not the full analytic partition function.
\item \textbf{Modular characteristic.}
The shadow tower uses $\kappa_{\mathrm{ch}} = 3$ (the modular
characteristic of the single-copy chiral algebra
$\Omega^{\mathrm{ch}}(K3 \times E)$, equal to
$\dim_\bC = 3$). The Igusa cusp form has weight
$\operatorname{wt}(\Phi_{10}) = 10 = 2\kappa_{\mathrm{BKM}}$
with $\kappa_{\mathrm{BKM}} = \chi(K3)/4 - 1 = 5$, the
second-quantized modular weight. The ratio
$\kappa_{\mathrm{BKM}}/\kappa_{\mathrm{ch}} = 5/3$ reflects
the passage from single-copy to symmetric-product via the
DMVV formula~\textup{\eqref{eq:dvv}}, and is specific to
$K3 \times E$ \textup{(}it is NOT a universal constant:
for the quintic, $\chi = -200$ gives a different ratio\textup{)}.
\item \textbf{Second quantization.}
The shadow tower is first-quantized: $F_g$ is the genus-$g$
amplitude of a \emph{single} copy of $\cA$. The partition
function $1/\Phi_{10}$ is second-quantized: it sums over
\emph{all} symmetric products $\operatorname{Sym}^N(K3)$
via the DMVV formula. The Borcherds lift,
the DMVV infinite product, and the symmetric-product
orbifold construction are second-quantized operations
not captured by the shadow tower alone.
\item \textbf{Schottky at $g \geq 4$.}
The Torelli map $j\colon \mathcal{M}_g \to \mathcal{A}_g$
has image of codimension $(g-2)(g-3)/2$ in~$\mathcal{A}_g$
for $g \geq 4$. Explicitly:
\begin{center}
\small
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{cccccccc}
$g$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ & $7$ \\
\hline
$\dim \mathcal{M}_g$ & $1$ & $3$ & $6$ & $9$ & $12$ & $15$ & $18$ \\
$\dim \mathcal{A}_g$ & $1$ & $3$ & $6$ & $10$ & $15$ & $21$ & $28$ \\
$\mathrm{codim}$ & $0$ & $0$ & $0$ & $1$ & $3$ & $6$ & $10$
\end{tabular}
\end{center}
For $g \leq 3$, the Torelli map is an isomorphism
($g = 1$), birational ($g = 2$), or injective with dense
image ($g = 3$), so the shadow tower sees essentially all
Siegel modular form data. At $g = 4$, the Schottky--Igusa
form of weight~$8$ vanishes precisely on the Jacobian locus
$\mathcal{J}_4 = j(\mathcal{M}_4)$: this is information
accessible to Siegel forms but invisible to the shadow tower.
For $g \to \infty$, the ratio
$\mathrm{codim}/\dim\mathcal{A}_g \to 1$: the Jacobian
locus becomes asymptotically negligible.
\end{enumerate}
\end{theorem}

\begin{proof}
(O1) is immediate from the definitions: $F_g \in \bQ$ while
$\Phi_{10}$ is a holomorphic function of three complex variables.
(O2) follows from the two independent computations
$\kappa_{\mathrm{ch}} = \dim_\bC = 3$
(Proposition~\ref{prop:shadow-k3e}) and
$\operatorname{wt}(\Phi_{10}) = 10$
(Definition~\ref{def:igusa-cusp-form}), together with the
identification $\kappa_{\mathrm{BKM}} = \chi(K3)/4 - 1 = 5$
from the DVV formula.
(O3) is the content of the DMVV formula: the
second equality in~\eqref{eq:dvv} expresses $1/\Phi_{10}$
as a sum over symmetric products, an operation external to
single-copy chiral algebra theory.
(O4): the codimension formula
$\mathrm{codim}(\mathcal{J}_g, \mathcal{A}_g)
= g(g+1)/2 - (3g-3) = (g-2)(g-3)/2$ for $g \geq 2$ is
classical (Riemann, Schottky).
\end{proof}

\begin{remark}[The genus-$2$ Torelli bridge]
\label{rem:torelli-bridge}
\index{Torelli map!genus-2 bridge}
At genus~$2$, the Torelli map
$j\colon \mathcal{M}_2 \to \mathcal{A}_2$ is birational:
its complement $\mathcal{A}_2 \setminus j(\mathcal{M}_2)$
is the product locus (abelian surfaces isomorphic to a
product of two elliptic curves). This means $\Phi_{10}$
restricts to a well-defined form on $\mathcal{M}_2$
(vanishing on the product locus at the boundary of the
Satake compactification), and the genus-$2$ partition
function $Z_2(\Omega)$ related to $1/\Phi_{10}$ has a
shadow amplitude
\[
F_2 = \int_{\overline{\mathcal{M}}_2} \kappa \cdot
\lambda_2^{\mathrm{FP}} = \frac{7}{1920}
\]
as its topological residue. The shadow $F_2$ is what
remains of $1/\Phi_{10}$ after integrating out all modular
dependence: a tautological intersection number in the
Chow ring of $\overline{\mathcal{M}}_2$.
\end{remark}

\subsection{Euler characteristic and Donaldson--Thomas structure}
\label{subsec:euler-dt}

\begin{proposition}[$\chi(K3 \times E) = 0$ and its consequences;
\ClaimStatusProvedElsewhere]
\label{prop:chi-zero}
\index{Euler characteristic!K3 x E}
\index{Donaldson--Thomas!K3 x E}
The Euler characteristic of $K3 \times E$ vanishes:
\[
\chi(K3 \times E) = \chi(K3) \cdot \chi(E)
= 24 \cdot 0 = 0.
\]
This has three structural consequences for the
enumerative geometry:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{MacMahon trivialization.}
The degree-$0$ DT partition function of a Calabi--Yau
threefold $X$ is $Z_{\mathrm{DT},0}(X) = M(-q)^{\chi(X)}$,
where $M(q) = \prod_{n \geq 1}(1-q^n)^{-n}$ is the
MacMahon function counting plane partitions. For
$\chi = 0$: $M(-q)^0 = 1$, so
$Z_{\mathrm{DT},0}(K3 \times E) = 1$. There is no
degree-$0$ contribution from plane-partition-type
combinatorics.
\item \emph{DT/PT correspondence.}
The vanishing $\chi = 0$ implies that the
Donaldson--Thomas and Pandharipande--Thomas partition
functions agree without a MacMahon prefactor correction:
\[
Z_{\mathrm{DT}}(K3 \times E)
= Z_{\mathrm{PT}}(K3 \times E).
\]
This is the ``clean'' case of the DT/PT wall-crossing
formula: the wall-crossing factor $M(-q)^{\chi}$ is trivial.
\item \emph{BCOV anomaly coefficient.}
The BCOV holomorphic anomaly coefficient
$\kappa_{\mathrm{BCOV}} = \chi(X)/24$ vanishes for
$K3 \times E$. The anomaly equation
$\bar{\partial}_{\bar{i}} F_g = \frac{1}{2}
C_{\bar{i}}^{\,jk}(D_j D_k F_{g-1} + \sum_{r=1}^{g-1}
D_j F_r\,D_k F_{g-r})$ is
therefore unobstructed at the topological level,
consistent with the shadow tower being controlled by the
single parameter $\kappa = 3$ without BCOV corrections.
\end{enumerate}
\end{proposition}

\begin{remark}[The four $\kappa$ invariants]
\label{rem:four-kappas}
\index{modular characteristic!four variants for K3 x E}
The preceding analysis exhibits four distinct invariants
that share the name ``$\kappa$'' in different parts of the
literature:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lll}
\textbf{Symbol} & \textbf{Value} & \textbf{Source} \\
\hline
$\kappa(\cA)$ & $3$ & Modular characteristic (Theorem~D) \\
$\kappa_{\mathrm{BCOV}}$ & $0$ & $\chi(K3 \times E)/24$ \\
$\kappa_{\mathrm{MacMahon}}$ & $0$ & Exponent of $M(-q)^{\chi}$ \\
$\kappa_{\mathrm{BKM}}$ & $5$ & $\operatorname{wt}(\Phi_{10})/2 = \chi(K3)/4 - 1$
\end{tabular}
\end{center}
These coincide for the Virasoro algebra
($\kappa = c/2$ in all r\^oles) but diverge for
$K3 \times E$. The modular characteristic $\kappa(\cA) = 3$
is the intrinsic invariant of the chiral algebra; the others
are geometric proxies valid in restricted contexts.
\end{remark}

\begin{remark}[Shadow depth classification]
\label{rem:bkm-shadow-depth}
\index{shadow depth!K3 x E}
The chiral algebra $\Omega^{\mathrm{ch}}(K3 \times E)$
has central charge $c = 6$, multiple generators of
varying conformal weight, and an infinite tower of OPE
coefficients from the $K3$ sigma model. By the
shadow depth classification
(Definition~\ref{def:shadow-depth-classification}),
$K3 \times E$ belongs to class~M (mixed, shadow depth
$r_{\max} = \infty$): the Borcherds product
formula~\eqref{eq:borcherds-lift} has infinitely many
distinct exponents $c_0(D)$, reflecting an infinite
sequence of independent shadow invariants. This is
consistent with the operadic complexity principle:
the sigma model on a Calabi--Yau target, being a fully
interacting CFT, has non-formal Swiss-cheese structure
at all degrees.
\end{remark}

\begin{remark}[Genus stratification summary]
\label{rem:genus-stratification}
\index{genus stratification!K3 x E}
The bridge between the shadow tower and Siegel modular
forms degrades with genus:
\begin{center}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{cll}
\textbf{Genus} & \textbf{Torelli} & \textbf{Shadow--Siegel status} \\
\hline
$1$ & Isomorphism & $F_1 = 1/8$ matches $\eta^{-6}$ exactly \\
$2$ & Birational & $F_2 = 7/1920$ is topological residue of $1/\Phi_{10}$ \\
$3$ & Injective, dense & $F_3$ captures most Siegel data \\
$\geq 4$ & Schottky obstructed & Shadow sees codim-$\frac{(g{-}2)(g{-}3)}{2}$ slice
\end{tabular}
\end{center}
The genus-$2$ case is the richest: the Torelli map is
almost an isomorphism, and $\Phi_{10}$ (the unique genus-$2$
cusp form of weight~$10$) is directly accessible. The
four obstructions of
Theorem~\ref{thm:shadow-siegel-gap} quantify exactly
what the shadow tower captures (the topological skeleton
$F_g = \kappa(\cA) \cdot \lambda_g^{\mathrm{FP}}$, ) and what it
misses (the analytic, second-quantized, and transverse-Siegel
content).
\end{remark}


%% ================================================================
\section{Costello's M2-brane model and the double-loop holographic dual}
\label{sec:m2-brane-double-loop}
\index{M2-brane!double-loop algebra}
\index{Costello!5d noncommutative Chern--Simons}
\index{holographic duality!bar-cobar as}

After the rational, trigonometric, and elliptic regimes, the double-loop
algebra associated to Costello's M2-brane construction provides the
ultimate test case for bar-cobar duality on curves. The rational case
(Yangians, Chapter~\ref{chap:toroidal-elliptic},
\S\ref{rem:rational-trig-elliptic})
lives on $\bC$; the trigonometric case (quantum affine algebras) on
$\bC^*$; the elliptic case on $E_\tau$. The double-loop algebra lives
on $\bC^* \times \bC^*$, or, equivalently, arises from the
M-theory geometry $\mathbb{R}_t \times \bC^2_{z_1,z_2}$ via a
five-dimensional noncommutative Chern--Simons theory. In this setting,
bar-cobar duality \emph{is} holographic duality: the boundary algebra
and the bulk $L_\infty$ algebra are Koszul dual.

\subsection{The 5d noncommutative Chern--Simons theory}

\begin{definition}[5d NCCS theory {\cite{Costello17}}; \ClaimStatusProvedElsewhere]
\label{def:5d-nccs}
\index{noncommutative Chern--Simons!5d theory}
Let $M_5 = \mathbb{R}_t \times \bC^2_{z_1,z_2}$ carry the
$\Omega$-background with deformation parameter $\varepsilon$.
The \emph{5d noncommutative Chern--Simons theory} has fields given by a
partial connection
\[
 A \;=\; A_t\,dt + A_{z_1}\,dz_1 + A_{z_2}\,dz_2,
\]
valued in $\mathfrak{gl}_r$ (or $\mathfrak{gl}_\infty$ in the large-$N$
limit), and action
\begin{equation}\label{eq:5d-nccs-action}
 S_{5d}(A)
 \;=\;
 \frac{1}{2\delta}\int \mathrm{Tr}\bigl(A \wedge dA\bigr)\,dz_1\,dz_2
 \;+\;
 \frac{1}{3\delta}\int \mathrm{Tr}\bigl(A \wedge A *_\varepsilon A\bigr)\,dz_1\,dz_2,
\end{equation}
where $*_\varepsilon$ denotes the Moyal star product on $\bC^2$
and $\delta$ is the coupling constant. An M2-brane wrapping
$\mathbb{R}_t \times \{(z_1,z_2) = (0,0)\}$ is realized as an
instanton particle of this 5d theory.
\end{definition}

\subsection{The classical double-current algebra}

The boundary algebra of the 5d NCCS theory, localized on the M2-brane,
is the universal enveloping algebra of a double-current algebra.

\begin{definition}[Double-current algebra]
\label{def:double-current-algebra}
\index{double-current algebra}
The \emph{double-current algebra} is the Lie algebra
\begin{equation}\label{eq:g-dbl}
 \fg_{\mathrm{dbl}}
 \;:=\;
 \mathfrak{gl}_r \otimes \bC[u,v]
\end{equation}
with generators $J^a_{m,n} := T^a \otimes u^m v^n$
(where $\{T^a\}$ is a basis for $\mathfrak{gl}_r$)
and bracket
\begin{equation}\label{eq:g-dbl-bracket}
 [J^a_{m,n},\; J^b_{p,q}]
 \;=\;
 f^{ab}{}_c\, J^c_{m+p,\,n+q}.
\end{equation}
The \emph{classical boundary algebra} is
$\cA^{\mathrm{cl}}_{\mathrm{M2}} := U(\fg_{\mathrm{dbl}})$.
\end{definition}

\begin{remark}[Bidegree and the double loop]
\label{rem:double-loop-bidegree}
The two polynomial indices $(m,n)$ in~\eqref{eq:g-dbl} encode the
``double loop'': $u$ parametrizes the $z_1$-direction and $v$ the
$z_2$-direction of $\bC^2$. In the
rational/trigonometric/elliptic hierarchy (Table~\ref{tab:rat-trig-ell}),
a single loop $\bC[u]$ gives affine Kac--Moody; the second loop
$\bC[v]$ gives toroidal algebras. The double-current algebra is the
classical ($q=1$) shadow of the full toroidal quantum group.
\end{remark}

\subsection{The Koszul dual bulk \texorpdfstring{$L_\infty$}{L-infinity} model}

\begin{proposition}[Classical Koszul duality for M2 boundary algebras; \ClaimStatusProvedElsewhere]
\label{prop:m2-classical-koszul}
\index{Koszul duality!M2-brane classical}
The bar construction applied to the classical boundary algebra yields
the bulk $L_\infty$ algebra:
\begin{equation}\label{eq:m2-bulk-classical}
 \cA^{\mathrm{cl}}_{\mathrm{bulk}}
 \;=\;
 \Omega\B\bigl(\cA^{\mathrm{cl}}_{\mathrm{M2}}\bigr)
 \;\simeq\;
 C^\bullet(\fg_{\mathrm{dbl}}),
\end{equation}
the Chevalley--Eilenberg cochain complex of $\fg_{\mathrm{dbl}}$.
In terms of dual generators $\epsilon^a_{m,n}$ dual to $J^a_{m,n}$,
the $L_\infty$ operations are:
\begin{align}
 \ell_1 &= 0, \label{eq:m2-ell1}\\
 \ell_2(\epsilon^a_{m,n},\, \epsilon^b_{p,q})
 &= f^{ab}{}_c\, \epsilon^c_{m+p,\,n+q},
 \label{eq:m2-ell2}\\
 \ell_{k} &= 0 \quad\text{for } k \geq 3
 \quad\text{(at the strict classical level).}
 \label{eq:m2-ellk}
\end{align}
\end{proposition}

\begin{proof}
The algebra $\cA^{\mathrm{cl}}_{\mathrm{M2}} = U(\fg_{\mathrm{dbl}})$
is a quadratic algebra whose Ext groups are computed via the bar complex:
$\mathrm{Ext}_{U(\fg_{\mathrm{dbl}})}(\bC, \bC)
\cong H^\bullet(\fg_{\mathrm{dbl}}, \bC)$.
By the PBW theorem, $U(\fg_{\mathrm{dbl}})$ is Koszul as a filtered
algebra, and cobar reconstruction gives~\eqref{eq:m2-bulk-classical}.
At the classical level the Lie algebra structure constants
$f^{ab}{}_c$ are the only datum, so only $\ell_2$ is non-trivial.
\end{proof}

\subsection{Quantum double-loop deformation}

\begin{proposition}[Costello's quantum double-loop commutation relation
{\cite{Costello17}}; \ClaimStatusProvedElsewhere]
\label{prop:costello-quantum-double-loop}
\index{double-current algebra!quantum deformation}
The quantum deformation of $\cA^{\mathrm{cl}}_{\mathrm{M2}}$ is a
filtered associative algebra $\cA_{\mathrm{M2}}^{\mathrm{q}}$ whose
generators satisfy
\begin{multline}\label{eq:costello-quantum-comm}
 [E_{\alpha\beta}\,\partial,\; E_{\gamma\delta}\,z]
 \;=\;
 \delta_{\beta\gamma}\,E_{\alpha\delta}(\partial z)
 \;-\;
 \delta_{\alpha\delta}\,E_{\gamma\beta}(z\partial)\\
 +\;\bar\hbar\,E_{\alpha\delta}\,E_{\gamma\beta}
 \;-\;
 \bar\hbar \sum_\mu \delta_{\beta\gamma}\,
 E_{\alpha\mu}\,E_{\mu\delta}
 \;-\;
 \bar\hbar \sum_\mu \delta_{\alpha\delta}\,
 E_{\gamma\mu}\,E_{\mu\beta},
\end{multline}
where $E_{\alpha\beta}$ are the standard matrix units of
$\mathfrak{gl}_r$ and $\bar\hbar$ is the quantum parameter.
This algebra is the unique filtered quantization of
$U(\fg_{\mathrm{dbl}})$ compatible with the
$\Omega$-background~\eqref{eq:5d-nccs-action}.
\end{proposition}

\begin{remark}[The quantum $\bar\hbar$-corrections]
\label{rem:quantum-hbar-corrections}
The three $\bar\hbar$-terms
in~\eqref{eq:costello-quantum-comm} are the boundary imprint of
the Moyal star product $*_\varepsilon$ in the bulk action
\eqref{eq:5d-nccs-action}. They encode the leading
non-commutativity of the double-loop algebra and are uniquely
determined by the requirement that the algebra be an associative
deformation of $U(\fg_{\mathrm{dbl}})$.
\end{remark}

\subsection{Sector/level/genus matching}

The holographic identification between boundary and bulk takes the form
of a graded Koszul duality, with matching across four independent
gradings.

\begin{conjecture}[Four-fold matching; \ClaimStatusConjectured]
\label{conj:m2-four-fold-matching}
\index{M2-brane!sector/level/genus matching}
The Koszul duality $\cA_{\mathrm{bulk}} =
\Omega\B(\cA_{\mathrm{M2}})$ respects the following matchings:
\begin{enumerate}
\item \emph{Sector-wise.} The adjoint label $a$ in the generator
 $J^a_{m,n}$ of the boundary algebra matches the dual label $a$ in
 the generator $\epsilon^a_{m,n}$ of the bulk $L_\infty$ algebra.
\item \emph{Level-wise.} The double-loop bidegree $(m,n)$ is
 preserved under bar-cobar duality: the $(m,n)$-component of
 $\cA_{\mathrm{M2}}$ is dual to the $(m,n)$-component of
 $\cA_{\mathrm{bulk}}$.
\item \emph{$N$-wise.} The finite-$N$ theory is obtained by
 quotienting:
 \begin{equation}\label{eq:m2-finite-N}
 \cA_{\partial,N}
 \;=\;
 \cA_{\partial,\infty}\big/I_N,
 \end{equation}
 where $I_N$ is the ideal of trace relations at rank $N$. The
 Koszul dual $\cA^!_{\partial,N} = D_{\mathrm{Ran}}(\B(\cA_{\partial,N}))$
 is the corresponding quotient of the dual boundary algebra.
\item \emph{Genus-wise.} The bulk $g$-loop corrections are the
 $\hbar^{g-1}$ terms in the $L_\infty$ operations $\ell_{g,n}$.
 In particular, the classical operations
 \eqref{eq:m2-ell1}--\eqref{eq:m2-ellk} correspond to
 tree level ($g=0$), and the first quantum correction
 $\ell_{1,n}^{(1)}$ to the one-loop bulk.
\end{enumerate}
Explicitly, for the generators at rank $\infty$:
\begin{equation}\label{eq:m2-explicit-koszul}
 \bigl(\cA_{\partial,\infty}(a;\,m,n)\bigr)^{!}
 \;\cong\;
 \cA_{\mathrm{bulk}}(a;\,m,n).
\end{equation}
\end{conjecture}

\begin{remark}[Bar-cobar duality as holographic duality]
\label{rem:bar-cobar-is-holographic}
\index{holographic duality!bar-cobar as|textbf}
The rational (Yangian), trigonometric
(quantum affine), and elliptic (toroidal) columns of
Table~\ref{tab:rat-trig-ell} converge on a single structural
fact: in Costello's M2-brane model, holographic duality is
\emph{Koszul duality}: the boundary algebra $\cA_\partial$
and its Koszul dual $\cA^!_\partial$ (obtained via Verdier
duality on bar cohomology) are identified with boundary and
bulk respectively. Bar-cobar inversion
$\Omega\B(\cA_\partial) \simeq \cA_\partial$ recovers the
boundary algebra itself (Theorem~B), not the bulk. The bulk
is the chiral derived centre
$C^\bullet_{\mathrm{ch}}(\cA_\partial, \cA_\partial)$.
The four-fold matching of
Conjecture~\ref{conj:m2-four-fold-matching} ensures that no
information is lost: sector, level, rank, and genus all transfer
across the duality.

This is the natural culmination of the chapter. The degeneration
chain~\eqref{eq:degeneration-chain} (elliptic $\to$ trigonometric
$\to$ rational) is supplemented by a fourth vertex: the double-loop
regime, in which the base geometry $\bC^* \times \bC^*$ supports a
genuine surface factorization algebra, and in which bar-cobar duality
acquires a direct physical interpretation as the AdS/CFT
correspondence for M2-branes.
\end{remark}
