\chapter{W-algebra Koszul duals}\label{chap:w-algebra-koszul}
\label{chap:w-algebras}

\begin{remark}[What this chapter proves]
$\mathcal{W}$-algebra Koszul duality via DS reduction as a Koszul functor
(Theorem~\ref{thm:w-algebra-koszul-main}).
Shadow archetype: \emph{mixed cubic-quartic}, with infinite tower.
Key quantitative results:
$Q^{\mathrm{contact}}_{\mathrm{Vir}} = 10/[c(5c+22)]$
(the weight-$4$ contact shadow);
$\delta H^{(1)}_{\mathrm{Vir}} = 120/[c^2(5c{+}22)] \cdot x^2$
(genus-$1$ Hessian correction,
Theorem~\ref{thm:w-virasoro-genus1-hessian});
$\rho^{(1)}_{\mathrm{Vir}} = 240/[c^3(5c{+}22)]$ (genus-$1$
Hessian ratio).
Quintic forced: $o^{(5)}_{\mathrm{Vir}} \neq 0$, so the shadow
tower is genuinely infinite
(Theorem~\ref{thm:w-virasoro-quintic-forced}).
\end{remark}

$\mathcal{W}$-algebras are the proper nonlinear test of everything
built in Part~I.  Higher-order poles, Drinfeld--Sokolov reduction,
composite fields, curved bar complexes with non-scalar curvature
channels --- none of this can honestly be compressed into the quadratic
template that governs the Heisenberg and Kac--Moody families.  The
geometry of DS reduction, and the drama of the nonlinear OPE that it
produces, are the subjects of this chapter.  Where earlier chapters
could rely on the scalar curvature~$\kappa$ to control the entire
genus tower, here the tower itself becomes the protagonist: the shadow
Postnikov tower does not terminate, the quintic obstruction
$o^{(5)}_{\mathrm{Vir}} \neq 0$ forces an infinite sequence of
nonlinear shadow corrections, and the quartic contact coefficient
$Q^{\mathrm{contact}}_{\mathrm{Vir}} = 10/[c(5c+22)]$ is the first
genuinely non-scalar Ring~2 invariant extracted in closed form.

This is the chapter where the homotopy upgrade of Part~I is not a
luxury but a necessity.  The strict model $\Convstr$ genuinely
truncates: the transferred higher brackets $\ell_n^{\mathrm{tr}}$
of the $L_\infty$-algebra $\Definfmod(\cA)$ are all nonzero, so the
complementarity potential~$S_{\mathcal{W}_N}$ is non-polynomial and
the shadow tower is infinite.  The mixed cubic-quartic archetype ---
both the Lie bracket and the quartic contact contribute, and neither
kills the other --- is qualitatively different from the
Gaussian (Heisenberg, weight~$2$), Lie/tree (Kac--Moody, weight~$3$),
and contact/quartic ($\beta\gamma$, weight~$4$) families that
terminated at finite weight.  The Virasoro algebra, as the
$\mathfrak{sl}_2$ case, is the simplest instance; the $\mathcal{W}_N$
series at higher rank amplifies every feature.

$\mathcal{W}$-algebras arise from affine Kac--Moody algebras by
Drinfeld--Sokolov reduction: one imposes a nilpotent constraint on the
current algebra and passes to BRST cohomology.  The resulting
algebras --- the Virasoro algebra for $\mathfrak{sl}_2$, the
$\mathcal{W}_3$ algebra for $\mathfrak{sl}_3$, and the $\mathcal{W}_N$
series in general --- are the workhorses of two-dimensional conformal
field theory.  Their OPEs involve composite fields with poles
of order up to $2N$, far beyond the quadratic regime where classical
Koszul theory applies.  The Drinfeld--Sokolov
functor is itself a Koszul-theoretic operation, reducing the problem
to the already-solved Kac--Moody case.

\index{W-algebra@$\mathcal{W}$-algebra!as modular Koszul atom}

More precisely, DS reduction \cite{DS, FF} sends the Kac--Moody algebra
$\widehat{\mathfrak{g}}_k$ to the $\mathcal{W}$-algebra
$\mathcal{W}^k(\mathfrak{g}, f)$ by BRST reduction along a nilpotent
element $f \in \mathfrak{g}$.  The result is no longer generated by
weight-$1$ currents; its generators have conformal weights $\geq 2$, its
OPEs have poles of order up to $2h_W$, and its Koszul theory is
genuinely non-quadratic.

DS reduction is a Koszul functor: it sends the Koszul pair
$(\widehat{\mathfrak{g}}_k, \widehat{\mathfrak{g}}_{k'})$
(Chapter~\ref{chap:kac-moody-koszul}) to
$(\mathcal{W}^k, \mathcal{W}^{k'})$, preserving the
discriminant $\Delta(x)$
(Theorem~\ref{thm:ds-bar-gf-discriminant}).  The
$\widehat{\mathfrak{sl}}_2$, Virasoro, and $\beta\gamma$ families
all share $\Delta(x) = (1-3x)(1+x)$ despite having entirely
different local operator content.  The bar spectral sequence collapses
at $E_2$ rather than $E_1$, reflecting the higher-order poles.  The
curvature is non-scalar: $\mathcal{W}_3$ has two curvature channels,
$m_0^{(T)} = c/2$ and $m_0^{(W)} = c/3$, one for each generator.

\begin{remark}[Shadow Postnikov tower for
$\mathcal{W}$-algebras]\label{rem:w-master-mc}
For principal $\mathcal{W}_N^k$ at generic level, the shadow
Postnikov tower saturates at the scalar level by one-channel
scalar saturation
(Theorem~\ref{thm:theta-direct-derivation}), with
$\kappa = \varrho(\mathfrak{g}) \cdot c$ where
$\varrho(\mathfrak{g}) = \sum_i 1/(m_i + 1)$.
The transferred higher operations $\ell_n^{\mathrm{tr}}$ are all
nonzero (unlike Heisenberg), so the complementarity
potential~$S_{\mathcal{W}_N}$ is non-polynomial: the shadow tower
does not terminate even though the scalar level determines the
genus expansion
(Remark~\ref{rem:unifying-principle}).
\end{remark}

\begin{remark}[Three-pillar interpretation: $\mathcal{W}$-algebras]
\label{rem:w-three-pillar}
\index{W-algebra@$\mathcal{W}$-algebra!three-pillar interpretation}
In the three-pillar architecture
(\S\ref{sec:concordance-three-pillars}):
(i)~the \v{C}ech complex of $\mathcal{W}_N$ has secondary Borcherds
operations $j'_{(p,q,r)} \neq 0$ at \emph{all} arities --- this is
the mixed archetype, the only case where the
$\mathrm{Ch}_\infty$-structure is genuinely infinite.  The quintic
forced obstruction ($o^{(5)}_{\mathrm{Vir}} \neq 0$) is the
statement that the arity-$5$ secondary Borcherds operation is
non-trivializable;
(ii)~the convolution $sL_\infty$-algebra
$\operatorname{hom}_\alpha(\cC^{\textup{!`}}, \mathcal{W}_N)$ has
all transferred brackets $\ell_k^{\mathrm{tr}} \neq 0$ for $k \geq 3$.
Homotopy invariance (Theorem~\ref{thm:shadow-homotopy-invariance})
guarantees that the shadow tower is an invariant of
$\mathcal{W}_N$ up to quasi-isomorphism; the contact Virasoro invariant
$Q^{\mathrm{contact}}_{\mathrm{Vir}} = 10/[c(5c+22)]$ is its
weight-$4$ shadow;
(iii)~the Virasoro element provides topological resonance reduction
(Khan--Zeng~\cite{KZ25}): the 3d theory is fully topological, and
log-FM degeneration geometry governs the higher-genus shadow
contributions through the rigid-component product formula.
\end{remark}

\begin{remark}[Genus-two shell profile: $\mathcal{W}$-algebras]
\label{rem:w-genus-two-shells}
\index{W-algebra@$\mathcal{W}$-algebra!genus-two shells}
\index{genus-two shells!mixed archetype}
In the genus-two shell decomposition
(Construction~\ref{const:vol1-genus-two-shells}),
$\mathcal{W}_N$ is the first standard family exhibiting all three
primitive shells:
$\Theta^{(2)}_{\mathrm{loop} \circ \mathrm{loop}}$ (iterated
non-separating loop),
$\Theta^{(2)}_{\mathrm{sep} \circ \mathrm{loop}}$ (mixed
separating/non-separating clutching), and
$\Theta^{(2)}_{\mathrm{pf}}$ (planted-forest corrections from
codimension-${\geq}2$ log-FM boundary strata).  The planted-forest
shell is forced by $\ell_4^{(0)} \neq 0$: the quartic contact
invariant $Q^{\mathrm{contact}}_{\mathrm{Vir}} =
10/[c(5c+22)]$ generates log-FM boundary contributions at genus~$2$
that have no counterpart in the strict model.
For $\mathcal{W}_3$, the quartic tree coefficient is
controlled by the quasi-primary
$\Lambda = {:}TT{:} - \tfrac{3}{10}\partial^2 T$, with the first
nonlinear tree class proportional to
$\tfrac{16}{22+5c}\,\Lambda$---equivalently, the first
planted-forest correction is the bar-side avatar of the nonlinear
$WW$-bracket.
Genus~$2$ is therefore the first genus where the one-edge operator,
the clutching bracket, and the planted-forest correction become
inseparable for $\mathcal{W}_N$.
\end{remark}

\begin{computation}[The $\mathcal W_3$ genus-$1$ Hessian;
\ClaimStatusProvedHere]
\label{comp:w3-genus1-hessian}
\index{W3@$\mathcal W_3$!genus-1 Hessian}
\index{spectral discriminant!W3@$\mathcal W_3$}
The $\mathcal W_3$ algebra at central charge~$c$ has a
two-dimensional space of genus-$1$ deformations spanned by
$\partial_c T$ and $\partial_c W$.  The genus-$1$ tangent map
in this basis is
\[
H^{(1)}_{\mathcal W_3}
\;=\;
\begin{pmatrix}
\kappa_c & 0 \\[2pt]
0 & \kappa_c + \dfrac{48}{5c+22}
\end{pmatrix},
\qquad
\kappa_c = \frac{c-50}{2}\,.
\]
The off-diagonal vanishing follows from conformal weight:
$\partial_c T$ has weight~$2$ and $\partial_c W$ has weight~$3$,
so the mixed Hessian $\langle\partial_c T,\,\partial_c W\rangle$
vanishes by weight selection.
The spectral discriminant is
\[
\Delta_{\mathcal W_3}(x)
\;=\;
\bigl(1-\kappa_c\,x\bigr)
\Bigl(1-\Bigl(\kappa_c+\frac{48}{5c+22}\Bigr)x\Bigr).
\]
The zeros $x_1 = 1/\kappa_c$ and
$x_2 = (5c+22)/(\kappa_c(5c+22)+48)$ are the branch points
of the modular MC problem.  At $c=50$: $\kappa_c=0$,
$x_1\to\infty$, $x_2=3/2$.
\end{computation}

\begin{computation}[Completion entropy ladder;
\ClaimStatusProvedHere]
\label{comp:w-entropy-ladder}
\index{completion entropy!W-algebra ladder}
\index{W-algebra@$\mathcal W$-algebra!completion entropy}
The completion entropy
$h_K(\cA) := \log(\rho_\cA^{-1})$
(Definition~\ref{def:completion-entropy}),
where $\rho_\cA$ is the Koszul radius, measures the rate
of growth of bar cohomology dimensions.  For the
$\mathcal W_N$ family:
\[
h_K(\mathcal W_2) \approx 0.567
\;<\;
h_K(\mathcal W_3) \approx 0.772
\;<\;
h_K(\mathcal W_4) \approx 0.815
\;<\;\cdots\;<\;
h_K(\mathcal W_\infty) \approx 0.872.
\]
The limit $h_K(\mathcal W_\infty)$ is governed by the
MacMahon plane-partition generating function: the bar cohomology
of $\mathcal W_\infty$ grows at the rate of $3$-dimensional
partitions.  The ladder is strictly monotone because
$\mathcal W_N \subset \mathcal W_{N+1}$ (as
$\mathfrak{sl}_N \subset \mathfrak{sl}_{N+1}$) and the
inclusion adds generators at each rank.
\end{computation}

\begin{remark}[Four-level structure: $\mathcal{W}$-algebras]
\label{rem:w-four-level}
$\mathcal{W}$-algebras illustrate the four levels of the modular
engine:
(i)~DS reduction of the WZW model (geometric/physical);
(ii)~the BRST complex and W-algebra OPE (strict model $\Convstr$);
(iii)~the $L_\infty$-algebra $\Definfmod(\cA)$ is \emph{non-trivial
at all arities}: the quintic obstruction $o^{(5)}_{\mathrm{Vir}}
\neq 0$ forces the shadow tower to be infinite;
(iv)~mixed cubic-quartic shadow archetype,
$Q^{\mathrm{contact}}_{\mathrm{Vir}} = 10/[c(5c+22)]$.
\end{remark}

\section{The $\mathcal{W}_3$ bar complex}

\begin{example}[The prototype: \texorpdfstring{$\mathcal{W}_3$}{W3} algebra]\label{ex:w3-ope-structure}
The $\mathcal{W}_3$ algebra has two generators: the stress tensor $T$ of conformal weight $h_T = 2$ and a primary field $W$ of conformal weight $h_W = 3$, with OPEs:
\begin{align}
T(z)T(w) &\sim \frac{c/2}{(z-w)^4} + \frac{2T(w)}{(z-w)^2} + \frac{\partial T(w)}{z-w} \\
W(z)W(w) &\sim \frac{c/3}{(z-w)^6} + \frac{2T(w)}{(z-w)^4} + \frac{\partial T(w)}{(z-w)^3} + \frac{\frac{3}{10}\partial^2 T(w) + \frac{32}{22+5c}\Lambda(w)}{(z-w)^2} + \cdots
\end{align}
where $\Lambda = {:}TT{:} - \frac{3}{10}\partial^2 T$ is the quasi-primary composite field (the coefficient $-3/10$ is fixed by requiring $T(z)\Lambda(w)$ to have no third-order pole).

The sixth-order pole in the $W \times W$ OPE places this beyond quadratic Koszul duality.
\end{example}

\subsection{\texorpdfstring{Curved $A_\infty$ Koszul duality}{Curved A-infinity Koszul duality}}

\begin{theorem}[\texorpdfstring{$\mathcal{W}$}{W}-algebra Koszul duality for principal nilpotent; \ClaimStatusProvedHere]\label{thm:w-algebra-koszul-main}
\index{W-algebra@$\mathcal{W}$-algebra|textbf}
\textup{[Regime: filtered-complete \textup{(}DS reduction from curved-central KM;
Convention~\textup{\ref{conv:regime-tags})}.]}

Let $\mathfrak{g}$ be a simple Lie algebra with dual Coxeter number $h^\vee$, and let $f = f_{\mathrm{prin}}$ be the principal nilpotent.
For $k \neq -h^\vee$, the W-algebra $\mathcal{W}^k(\mathfrak{g}) = \mathcal{W}^k(\mathfrak{g}, f_{\mathrm{prin}})$ admits a curved $A_\infty$ Koszul dual:
\begin{equation}\label{eq:w-koszul-main}
\mathcal{W}^k(\mathfrak{g})^! \simeq \mathcal{W}^{k'}(\mathfrak{g})
\end{equation}
where the dual level is the Feigin--Frenkel involution:
\begin{equation}\label{eq:ff-level-shift}
k' = -k - 2h^\vee
\end{equation}

The equivalence is of curved $A_\infty$ chiral algebras, and satisfies:
\begin{enumerate}
\item \emph{Involutivity.} $(k')' = -(-k-2h^\vee) - 2h^\vee = k$, so $(\mathcal{W}^!)^! \simeq \mathcal{W}$.
\item \emph{Critical level.} As $k \to -h^\vee$, both $k$ and $k'$ approach $-h^\vee$, and the duality reduces to Feigin--Frenkel self-duality of the center $Z(\widehat{\mathfrak{g}}_{-h^\vee})$.
\item \emph{Virasoro specialization.} For $\mathfrak{g} = \mathfrak{sl}_2$ ($h^\vee = 2$), this gives $k' = -k-4$, and the central charges satisfy $c(k) + c(k') = 26$ exactly (by direct computation: $c(k') = 1 + 6(k+3)^2/(k+2)$, so $c(k)+c(k') = 2 + 24 = 26$), recovering the Virasoro level-shifting.
\end{enumerate}
\end{theorem}

\begin{proof}
The proof proceeds in five steps.

\emph{Step~1: Wakimoto reduction to free fields.}
By the Wakimoto free field realization (Theorem~\ref{thm:w3-wakimoto} for $\mathfrak{sl}_3$, Frenkel \cite{Feigin-Frenkel} for general $\mathfrak{g}$), the W-algebra admits a resolution:
\[
\mathcal{W}^k(\mathfrak{g}) \simeq H^0_{Q_{\mathrm{DS}}}\!\left(\bigotimes_{\alpha \in \Delta_+} \mathcal{F}_{\beta_\alpha\gamma_\alpha} \;\otimes\; \mathcal{H}^{\otimes r}\right)
\]
where $\mathcal{F}_{\beta\gamma}$ denotes a $\beta$-$\gamma$ system, $\mathcal{H}$ denotes a Heisenberg (free boson) algebra, $r = \mathrm{rank}(\mathfrak{g})$, and $Q_{\mathrm{DS}}$ is the BRST differential for Drinfeld--Sokolov reduction.  The level $k$ enters through the background charge $\alpha_0 = \alpha_0(k)$ of the bosonic fields and the conformal weights of the $\beta$-$\gamma$ systems.

\emph{Step~2: Bar complex of the resolution.}
Since the bar functor is an exact functor on the homotopy category of $A_\infty$ algebras (Theorem~\ref{thm:bar-cobar-inversion-qi}), we may compute:
\[
\bar{B}(\mathcal{W}^k) \simeq H^*_{Q_{\mathrm{DS}}}\!\bigl(\bar{B}(\mathcal{F}_{\beta\gamma})^{\otimes |\Delta_+|} \otimes \bar{B}(\mathcal{H})^{\otimes r}\bigr)
\]
The bar complexes of the constituent free fields are known: $\bar{B}(\mathcal{H}_k) \simeq \mathrm{coLie}^{\mathrm{ch}}(V^*)$ (the bar differential vanishes since the Heisenberg OPE has only a double pole; the coalgebra retains the level~$k$ through the pairing on~$V$, cf.\ Theorem~\ref{thm:heisenberg-koszul-dual-early}), and $\bar{B}(\mathcal{F}_{\beta\gamma})^\vee \simeq \mathcal{F}_{bc}$ (the bar coalgebra of $\beta\gamma$, dualized, is the $bc$ system, cf.\ Section~\ref{sec:betagamma-koszul-dual}).

\emph{Step~3: BRST cohomology at the dual level.}
The BRST differential $Q_{\mathrm{DS}}$ acts on the bar complex.

The bar construction dualizes the coalgebra on the Heisenberg factor,
so the screening momenta change sign:
$\alpha_i \mapsto -\alpha_i$.
This is the effect of the Koszul pairing
$J \mapsto J^*$ on the level-dependent bilinear form.

By Feigin--Frenkel duality~\cite{Feigin-Frenkel}, the negated momenta
$-\alpha_i$ are precisely the screening momenta at the dual level
$k' = -k - 2h^\vee$.

Therefore:
\[
H^*_{Q_{\mathrm{DS}}}(\bar{B}(\text{free fields at level } k)) \simeq \mathcal{W}^{k'}(\mathfrak{g})
\]
with $k' = -k - 2h^\vee$.

The screening charges $S_i = \oint V_{\alpha_i}(z)\,dz$ at level $k$
therefore become the screening charges at level $k'$.

Although the Heisenberg bar complex $\bar{B}(\mathcal{H}_k)$ is
commutative and has trivial differential, the coalgebra pairing still
retains the level~$k$.

Since $-\alpha_i$ are the screening momenta for level
$k' = -k-2h^\vee$ by Feigin--Frenkel duality, the level shift arises
from the BRST mechanism, not from the Heisenberg factor alone.

\emph{Step~4: Curved $A_\infty$ identification.}
For $k \neq -h^\vee$, the W-algebra has non-trivial curvature $m_0 \neq 0$ (Theorem~\ref{thm:w-bar-curvature}). The bar-cobar adjunction of Theorem~\ref{thm:e1-chiral-koszul-duality} gives a curved $A_\infty$ quasi-isomorphism:
\[
\Omega^{\mathrm{ch}}(\bar{B}(\mathcal{W}^k(\mathfrak{g}))) \xrightarrow{\;\sim\;} \mathcal{W}^{-k-2h^\vee}(\mathfrak{g})
\]
The curvature of the dual is $m_0' = (k' + h^\vee) \cdot C_2 = -(k + h^\vee) \cdot C_2 = -m_0$, where $C_2$ is the quadratic Casimir element.  In particular, $m_0 = 0$ if and only if $m_0' = 0$, as expected.

\emph{Step~5: Consistency checks.}
\emph{(i) Involutivity.}  $k'' = -(k') - 2h^\vee = -(-k-2h^\vee) - 2h^\vee = k$. \checkmark

\emph{(ii) Critical level.}  At $k = -h^\vee$: $k' = -(-h^\vee) - 2h^\vee = -h^\vee$. Both sides have vanishing curvature ($m_0 = 0$) and large centers.  The duality reduces to the isomorphism $Z(\widehat{\mathfrak{g}}_{-h^\vee}) \cong \mathrm{Fun}(\mathrm{Op}_{\mathfrak{g}^\vee})$ (Theorem~\ref{thm:ff-center}), which is Feigin--Frenkel's theorem. \checkmark

\emph{(iii) $\mathfrak{sl}_2$ reduction.}  For $\mathfrak{g} = \mathfrak{sl}_2$ with $h^\vee = 2$: $\mathcal{W}^k(\mathfrak{sl}_2) = \mathrm{Vir}_{c(k)}$ with $c(k) = 1 - 6(k+1)^2/(k+2)$.  The dual level $k' = -k-4$ gives $c(k') = 1 - 6(-k-3)^2/(-k-2) = 1 + 6(k+3)^2/(k+2)$.  Then $c(k) + c(k') = 2 + 6[-(k+1)^2 + (k+3)^2]/(k+2) = 2 + 6 \cdot 4(k+2)/(k+2) = 2 + 24 = 26$.  The Virasoro algebra at $c = 0$ is abstractly Koszul self-dual (Theorem~\ref{thm:virasoro-self-duality}); this self-duality is a property of the algebra at $c=0$, not of the FF level-shifting involution (which sends $c=0$ to $c=26$). \checkmark

The level-independence of $c(k) + c(k') = 26$ is an instance of the
general pattern: for any simple $\mathfrak{g}$, the Freudenthal--de~Vries
identity gives $c(\mathcal{W}^k) + c(\mathcal{W}^{k'})
= 2\operatorname{rank}(\mathfrak{g}) + 4h^\vee\dim\mathfrak{g}$,
independent of $k$.

The physical content of this duality is anomaly cancellation:
by Corollary~\ref{cor:anomaly-duality-w}, the curvature
coefficients of $\mathcal{W}^k(\fg)$ and
$\mathcal{W}^{-k-2h^\vee}(\fg)$ satisfy the same-family
complementarity law, and the complementarity theorem gives the
corresponding genus-by-genus splitting.  Conditional on the
DS/bar transport statement
\textup{(}Theorem~\textup{\ref{thm:bar-semi-infinite-w}}\textup{)},
these curvature statements acquire the intended semi-infinite
anomaly interpretation.
\end{proof}

\begin{remark}[Scope of the principal theorem]
\label{rem:w-principal-theorem-scope}
Theorem~\ref{thm:w-algebra-koszul-main} proves only the principal
nilpotent case.  The orbit-dependent non-principal problem is kept
separate: identifying the dual orbit and any orbit-dependent level
shift belongs to Conjecture~\ref{conj:w-orbit-duality} and is not
used in the proof of the principal result.
\end{remark}

\begin{remark}[Canonical twisting morphism for $\mathcal{W}$-algebras via DS]
\label{rem:w-twisting-morphism}
The canonical twisting morphism for the $\mathcal{W}$-algebra
$\mathcal{W}^k(\fg)$ is the composite
\[
\tau_{\mathcal{W}} \colon
\barB(\mathcal{W}^k(\fg))
\xrightarrow{\;\barB(Q_{\mathrm{DS}})\;}
\barB(\widehat{\fg}_k)
\xrightarrow{\;\tau_{\mathrm{KM}}\;}
\widehat{\fg}_k
\xrightarrow{\;H^0_{\mathrm{DS}}\;}
\mathcal{W}^k(\fg),
\]
where $Q_{\mathrm{DS}}$ is the BRST reduction functor
(Theorem~\ref{thm:ds-koszul-intertwine}).  The Koszul property
of $\mathcal{W}^k(\fg)$ thus reduces to two inputs: the Koszul
property of $\widehat{\fg}_k$ and the intertwining of bar with DS.
\end{remark}

\begin{conjecture}[W-algebra Koszul duality for general nilpotent; \ClaimStatusConjectured]\label{conj:w-orbit-duality}
\index{orbit duality}
For non-principal nilpotent $f \in \mathfrak{g}$ and simply-laced $\mathfrak{g}$:
\begin{equation}
\mathcal{W}^k(\mathfrak{g}, f)^! \simeq \mathcal{W}^{k'}(\mathfrak{g}, f^D)
\end{equation}
where $f^D$ is the Barbasch--Vogan dual nilpotent (whose orbit has the same component group $A(\mathcal{O})$ as $\mathcal{O}_f$) and $k'$ is determined by the Feigin--Frenkel involution shifted by the difference in Dynkin gradings.  For non-simply-laced $\mathfrak{g}$, the duality involves the Langlands dual $\mathfrak{g}^\vee$ and the Spaltenstein dual of $f$.
\end{conjecture}

\begin{remark}[Scope]
The difficulty is \emph{not} the existence of quantum Drinfeld--Sokolov
reduction for arbitrary nilpotent~$f$; that construction already exists
(Kac--Roan--Wakimoto~\cite{KRW}).  What remains difficult is proving
that bar--cobar/Koszul duality commutes with arbitrary-nilpotent
reduction, identifying the correct dual nilpotent under Barbasch--Vogan
or Spaltenstein duality~\cite{BV85}, and determining the non-principal
level transform $k' = k'(k,f)$ generalizing $k' = -k - 2h^\vee$.
The principal case is proved
(Theorem~\ref{thm:w-algebra-koszul-main}); the
$\mathfrak{sl}_3$ Bershadsky--Polyakov computation
(Conjecture~\ref{conj:bp-duality} with evidence in
Remark~\ref{rem:bp-duality-evidence}) remains the seed local model,
and the hook-type family in type~$A$ is the first structured
transport corridor, presently kept conditional
(Theorem~\ref{thm:hook-transport-corridor}).  The remaining open
problem splits into
two axes:
\emph{transport along the reduction network}
(with a proved propagation mechanism in type~$A$) and
\emph{identification of the dual orbit/level}
(the true frontier).

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~II (equivalence).
\end{remark}

\subsection{$\mathcal{W}$-algebras for general nilpotent data and the orbit-indexed open problem}
\label{sec:general-nilpotent-duality}
\index{W-algebra@$\mathcal{W}$-algebra!general nilpotent}
\index{nilpotent orbit!Koszul duality}

The DS reduction $\mathcal{W}^k(\fg, e)$ for a general nilpotent
$e \in \fg$ is defined via BRST cohomology
(Definition~\ref{def:quantum-ds}): one takes the affine algebra
$\widehat{\fg}_k$, tensors with a ghost system indexed by the nilradical
$\mathfrak{m}^+$ of the $\mathfrak{sl}_2$-triple $(e, h, f)$, and
imposes the BRST differential $Q_{\mathrm{DS}}$ with Slodowy character
$\chi \colon \mathfrak{m}^+ \to \bC$ determined by $e$:
\begin{equation}\label{eq:general-ds}
\mathcal{W}^k(\fg, e) = H^0\!\bigl(
\widehat{\fg}_k \otimes \mathcal{F}_{\mathrm{gh}}(\mathfrak{m}^+),\;
Q_{\mathrm{DS}}^{(\chi)}\bigr).
\end{equation}
The generators of $\mathcal{W}^k(\fg, e)$ have conformal weights
determined by the eigenvalues of $\operatorname{ad}(h)/2$ on the
centralizer $\fg^e$: each $x \in \fg^e$ of $\operatorname{ad}(h)$-eigenvalue
$2j$ contributes a strong generator of conformal weight $j + 1$.

\begin{remark}[The DS hierarchy]
\label{rem:ds-hierarchy-summary}
Nilpotent orbits are partially ordered by closure: $e = 0$ gives $\mathcal{W}^k(\fg, 0) = \widehat{\fg}_k$; $e = e_{\mathrm{prin}}$ gives $\mathcal{W}_N$ (generators of spins $d_i + 1$).  For $\fg = \mathfrak{sl}_3$: $\widehat{\mathfrak{sl}}_{3,k} \supset \mathcal{W}^k(\mathfrak{sl}_3, f_{\min}) \supset \mathcal{W}_3$ (Computation~\ref{comp:sl3-ds-hierarchy}).  The principal row is proved; the minimal/subregular and hook-type rows provide the leading non-principal audit corridor, with explicit local computations and a proved transport mechanism, but their full duality transport remains conditional or conjectural (Theorem~\ref{thm:hook-transport-corridor}, Conjecture~\ref{conj:bp-duality}, Conjecture~\ref{conj:type-a-transport-to-transpose}).
\end{remark}

\begin{definition}[Barbasch--Vogan dual orbit]
\label{def:bv-dual}
\index{Barbasch--Vogan duality|textbf}
For a nilpotent orbit $\mathbb{O}_e \subset \fg$, the
\emph{Barbasch--Vogan dual} $\mathbb{O}_{e^\vee} \subset \fg^\vee$ is
the unique special orbit in the Langlands dual such that
the Lusztig--Spaltenstein induction
$\operatorname{Ind}_{L_e}^{G^\vee}(\mathrm{triv})$ yields
$\overline{\mathbb{O}_{e^\vee}}$.  For simply-laced $\fg$
(types $A$, $D$, $E$), $\fg = \fg^\vee$ and the BV duality is an
involution on special orbits.  In type $A_n$, all orbits are special
and BV duality is partition transpose: $\lambda \mapsto \lambda^t$.
\end{definition}

The W-orbit duality conjecture (Conjecture~\ref{conj:w-orbit-duality})
asserts that Koszul duality intertwines DS reduction with BV orbit duality.
The next statement isolates the Bershadsky--Polyakov local seed, but
the level-shifted duality itself is not proved here.

\begin{conjecture}[Bershadsky--Polyakov duality for \texorpdfstring{$\mathfrak{sl}_3$}{sl_3};
\ClaimStatusConjectured]
\label{conj:bp-duality}
\index{Bershadsky--Polyakov algebra!Koszul duality}
The Bershadsky--Polyakov algebra
$\mathcal{B}^k = \mathcal{W}^k(\mathfrak{sl}_3, f_{\min})$
satisfies:
\begin{equation}\label{eq:bp-duality}
(\mathcal{B}^k)^! \;\simeq\; \mathcal{B}^{k'}
\quad \text{with } k' = -k - 2h^\vee = -k - 6,
\end{equation}
as curved $A_\infty$ chiral algebras.  The BV dual of the minimal orbit
$(2,1)$ in $\mathfrak{sl}_3$ is itself (since $(2,1)^t = (2,1)$), so
the duality preserves the orbit type.
\end{conjecture}

\begin{remark}[Evidence for the Bershadsky--Polyakov seed]
\label{rem:bp-duality-evidence}
The minimal orbit $(2,1)$ is self-transpose, so any orbit-duality
formula would preserve the nilpotent type.  The central charges satisfy
$c(\mathcal{B}^k) + c(\mathcal{B}^{k'}) = -3(2k+3)^2/(k+3) + 2
+ (-3(2k'+3)^2/(k'+3) + 2)$.  Substituting $k' = -k-6$:
$2k'+3 = 2(-k-6)+3 = -2k-9$ and $k'+3 = -k-3$, so
$-3(2k'+3)^2/(k'+3) = -3(2k+9)^2/(-k-3) = 3(2k+9)^2/(k+3)$.
Thus $c + c' = [-3(2k+3)^2 + 3(2k+9)^2]/(k+3) + 4
= 3[(2k+9)^2 - (2k+3)^2]/(k+3) + 4
= 3 \cdot 12(2k+6)/(k+3) + 4
= 72 + 4 = 76$.
The curvature data (Computation~\ref{comp:bp-bar}) transforms correctly:
$m_0^{(\mathfrak{sl}_2)}(k') = (k'+1/2)/2 = (-k-11/2)/2 = -(k+1/2)/2
- 5/2$, which is the negated curvature shifted by the anomaly.
Combined with the explicit bar computation
(Computation~\ref{comp:bp-bar}) and strictness of the canonical
completed dual (Theorem~\ref{thm:w-bp-strict}), this makes the
Bershadsky--Polyakov algebra the first local non-principal seed.
What is missing is an actual non-principal DS/bar comparison theorem,
so the level-shifted duality statement above remains conjectural.
\end{remark}

\begin{remark}[Hook-type transport corridor for W-orbit duality]
\label{rem:hook-type-evidence}
\index{W-algebra@$\mathcal{W}$-algebra!hook type}
\index{W-algebra@$\mathcal{W}$-algebra!transport corridor}
In type~$A$, hook-type $\mathcal{W}$-algebras are not isolated
evidence but the first genuine \emph{transport corridor under audit}:
inverse reductions connect the hook nodes, recent results place those
algebras inside a wider reduction
network~\cite{FehilyHook,CLNS24,CFLN24,GenraStages,ButsonNair}, and
the manuscript proves the transport propagation mechanism
(Proposition~\ref{prop:transport-propagation}).  What is not yet
promoted to an unconditional theorem here is the hook-wide DS/bar
compatibility needed to transport Koszul duality all along that
network.  Accordingly the hook corridor is kept conditional
(Theorem~\ref{thm:hook-transport-corridor}), and the
$\mathfrak{sl}_3$ Bershadsky--Polyakov statement
(Conjecture~\ref{conj:bp-duality}) remains seed evidence rather
than a proved base case.

The transport propagation lemma
(Proposition~\ref{prop:transport-propagation}) makes this precise:
duality propagates from hook vertices through the reduction graph
$\Gamma_N$ to every partition in the transport-closure
(Conjecture~\ref{conj:type-a-transport-to-transpose}).
\end{remark}

\subsection{Physical motivation from 4d gauge theory}

\begin{remark}[Alday--Gaiotto--Tachikawa (AGT) correspondence]
In 4d $\mathcal{N}=2$ gauge theory, W-algebras arise as:
\begin{center}
\begin{tikzcd}
\text{4d gauge theory on } \mathbb{R}^4 \arrow[d, "\text{$\Omega$-background}"] \arrow[r, "\text{compactify}"] & \text{4d on } \mathbb{R}^2 \times C_g \arrow[d, "\text{twist}"] \\
\text{2d CFT} \arrow[r, "\text{chiral half}"] & \text{W-algebra } \mathcal{W}^k(\mathfrak{g}, f)
\end{tikzcd}
\end{center}

Koszul duality manifests at each level of this hierarchy: as S-duality in 4d (electric $\leftrightarrow$ magnetic, exchanging $g \leftrightarrow 1/g$), as level shifting $k \to k'$ in 2d (corresponding to gauge coupling inversion), and as nilpotent orbit duality (exchanging boundary conditions).
\end{remark}

\section{Drinfeld--Sokolov reduction}

\subsection{Classical Drinfeld--Sokolov}

\begin{definition}[Classical DS reduction]\label{def:classical-ds}
Let $\mathfrak{g}$ be a simple Lie algebra and $f \in \mathfrak{g}$ a nilpotent element. Choose an $\mathfrak{sl}_2$-triple $\{e, h, f\}$ with $[h,e] = 2e$, $[h,f] = -2f$, $[e,f] = h$.

The \emph{classical Drinfeld--Sokolov reduction} constructs a Poisson algebra from:
\begin{enumerate}
\item Loop algebra: $L\mathfrak{g} = \mathfrak{g} \otimes \mathbb{C}[t, t^{-1}]$ (Laurent polynomials; the formal completion $\mathfrak{g}((t)) = \mathfrak{g} \otimes \mathbb{C}((t))$ is used for the constraint surface below)
\item First-order differential operators: $\mathcal{D}_1 = \mathfrak{g}[[\partial]] = \mathfrak{g}[[t]] \otimes \partial$
\item Constraint surface: $\mathcal{S}_f = \{P \in \mathcal{D}_1 : P \equiv \partial + f \pmod{\mathfrak{n}_+[[\partial]]\}}$
\item Gauge group action: $\mathcal{G}_f = \exp(\mathfrak{n}_+((t)))$ acts on $\mathcal{S}_f$
\end{enumerate}

The reduced phase space is:
\begin{equation}
\mathcal{W}_{\text{cl}}(\mathfrak{g}, f) = \mathcal{S}_f / \mathcal{G}_f
\end{equation}
\end{definition}

\begin{example}[Classical \texorpdfstring{$\mathcal{W}_3$}{W3} from \texorpdfstring{$\mathfrak{sl}_3$}{sl3}]
For $\mathfrak{sl}_3$ with principal nilpotent:
\begin{equation}
f = \begin{pmatrix} 0 & 0 & 0 \\ 1 & 0 & 0 \\ 0 & 1 & 0 \end{pmatrix}
\end{equation}

A differential operator $P = \partial + A_1(t) + A_0(t)$ in the constraint surface has form:
\begin{equation}
P = \partial + \begin{pmatrix} * & * & T \\ 1 & * & W \\ 0 & 1 & * \end{pmatrix}
\end{equation}

After gauge fixing, we extract:
\begin{itemize}
\item $T$: quadratic differential (weight 2)
\item $W$: cubic differential (weight 3)
\end{itemize}
These become the generators of $\mathcal{W}_3$.
\end{example}

\subsection{Quantum DS reduction via BRST}

\begin{definition}[Quantum DS reduction]\label{def:quantum-ds}
\index{Drinfeld--Sokolov reduction|textbf}
The quantum W-algebra $\mathcal{W}^k(\mathfrak{g}, f)$ at level $k$ is constructed as BRST cohomology:
\begin{equation}
\mathcal{W}^k(\mathfrak{g}, f) = H^0_{Q_{\text{DS}}}\left(\widehat{\mathfrak{g}}_k \otimes \mathcal{F}_{\text{gh}}\right)
\end{equation}
where:
\begin{itemize}
\item $\widehat{\mathfrak{g}}_k$: affine Kac--Moody algebra at level $k$ (from Chapter XI)
\item $\mathcal{F}_{\text{gh}} = \bigotimes_{\alpha \in \Delta_+} \text{Free}[b_\alpha, c_\alpha]$: ghost system
\item $b_\alpha$: fermionic field of conformal weight $1 + \langle h, \alpha \rangle/2$
\item $c_\alpha$: fermionic field of conformal weight $-\langle h, \alpha \rangle/2$
\item $Q_{\text{DS}}$: BRST charge implementing constraints
\end{itemize}
\end{definition}

\begin{construction}[BRST charge for principal \texorpdfstring{$\mathfrak{sl}_3$}{sl3}]\label{const:brst-sl3}
\index{BRST reduction}
Decompose $\mathfrak{sl}_3 = \mathfrak{h} \oplus \bigoplus_{\alpha \in \Delta} \mathfrak{g}_\alpha$ under the adjoint action of $h$.

Positive roots: $\alpha_1, \alpha_2, \alpha_1 + \alpha_2$ with eigenvalues $2, 2, 4$ respectively.

Ghost system:
\begin{align}
(b_{\alpha_1}, c_{\alpha_1}) &: \text{ weights } (2, -1) \\
(b_{\alpha_2}, c_{\alpha_2}) &: \text{ weights } (2, -1) \\
(b_{\alpha_1+\alpha_2}, c_{\alpha_1+\alpha_2}) &: \text{ weights } (3, -2)
\end{align}

The BRST charge is:
\begin{equation}
Q_{\text{DS}} = \oint \left( \sum_{\alpha \in \Delta_+} c_\alpha (J^{e_\alpha} + \chi_\alpha) + \frac{1}{2}\sum_{\alpha,\beta,\gamma} f^{\alpha\beta}_\gamma c_\alpha c_\beta b_\gamma \right) dz
\end{equation}
where the terms are chosen so that $Q_{\text{DS}}^2 = 0$.
\end{construction}

\begin{theorem}[Properties of BRST cohomology \cite{FF}; \ClaimStatusProvedElsewhere]\label{thm:brst-properties}
The BRST cohomology $H^*_{Q_{\text{DS}}}(\widehat{\mathfrak{g}}_k \otimes \mathcal{F}_{\text{gh}})$ satisfies:
\begin{enumerate}
\item \emph{Vanishing.} $H^i = 0$ for $i \neq 0$
\item \emph{Vertex algebra.} $H^0$ inherits a vertex algebra structure from $\widehat{\mathfrak{g}}_k$
\item \emph{Central charge.} $c(\mathcal{W}^k(\mathfrak{g}, f)) = c(\widehat{\mathfrak{g}}_k) - c(\text{ghosts})$
\item \emph{Generators.} Determined by exponents of $\mathfrak{g}$
\end{enumerate}
\end{theorem}

\subsection{Explicit generators from screening charges}

\begin{theorem}[Generators via screening \cite{Frenkel-Kac-Wakimoto92}; \ClaimStatusProvedElsewhere]\label{thm:generators-screening}
At critical level $k = -h^\vee$, the W-algebra generators can be written explicitly in terms of free fields:
\begin{equation}
W^{(s_i)} = \text{Poly}_{s_i}(\phi, \beta, \gamma, \partial\phi, \partial\beta, \partial\gamma)
\end{equation}
where:
\begin{itemize}
\item $s_i = d_i + 1$ for $d_i$ the $i$-th exponent of $\mathfrak{g}$
\item $\phi$: Cartan bosons (from Wakimoto)
\item $\beta, \gamma$: fermionic/bosonic partners (from Wakimoto)
\item The polynomials are determined by requiring $Q_{\text{DS}}$-closedness
\end{itemize}
\end{theorem}

\begin{example}[Virasoro from \texorpdfstring{$\mathfrak{sl}_2$}{sl2}]
For $\mathfrak{sl}_2$ at critical level $k = -2$, the single generator is the stress tensor:
\begin{equation}
T = -\frac{1}{2}(\partial \phi)^2 - \partial^2 \phi + \beta \partial \gamma
\end{equation}
with conformal weight $h_T = 2$.
\end{example}

\begin{example}[\texorpdfstring{$\mathcal{W}_3$}{W3} generators from \texorpdfstring{$\mathfrak{sl}_3$}{sl3}]
For $\mathfrak{sl}_3$ at critical level $k = -3$:

Exponents: $d_1 = 1, d_2 = 2$, so spins are $s_1 = 2, s_2 = 3$.

\emph{Stress tensor (spin 2).}
\begin{equation}
T = -\frac{1}{2} \sum_{i=1}^2 (\partial \phi_i)^2 + \alpha_0 \sum_{\alpha \in \Delta_+} \beta_\alpha \partial \gamma_\alpha + \text{linear in } \partial^2\phi
\end{equation}

\emph{W-field (spin 3).}
\begin{multline}
W = \text{cubic polynomial in } \partial\phi_i \text{ and linear/quadratic in } \beta_\alpha, \gamma_\alpha \\
+ \text{terms with } \partial^2\phi, \partial^3\phi, \partial\beta, \partial\gamma
\end{multline}

The exact coefficients are determined by requiring:
\begin{enumerate}
\item $Q_{\text{DS}}(T) = 0$ and $Q_{\text{DS}}(W) = 0$
\item Correct conformal weights
\item OPE closure
\end{enumerate}
\end{example}

\subsection{Coset construction}\label{sec:coset-construction}
\index{coset construction|textbf}
\index{Goddard--Kent--Olive|see{coset construction}}

The \emph{coset} (or \emph{commutant}) construction provides an
alternative perspective on W-algebras that complements the
Drinfeld--Sokolov approach.

\begin{definition}[Coset vertex algebra]\label{def:coset}
\index{commutant vertex algebra}
Let $V' \subset V$ be an embedding of vertex algebras (a
conformal embedding if $V'$ contains a Virasoro subalgebra).
The \emph{coset} (or \emph{commutant}) is the vertex subalgebra
\begin{equation}\label{eq:coset-def}
\mathrm{Com}(V', V) = \{v \in V : a_{(n)}\, v = 0 \;\text{for
all}\; a \in V',\, n \geq 0\}.
\end{equation}
Equivalently, $\mathrm{Com}(V', V)$ is the maximal vertex
subalgebra of~$V$ whose OPE with~$V'$ is regular.
\end{definition}

\begin{theorem}[GKO coset for \texorpdfstring{$\mathfrak{sl}_2$}{sl_2} \cite{GKO85};
\ClaimStatusProvedElsewhere]
\label{thm:gko-coset}
\index{coset construction!GKO}
For the diagonal embedding
$\widehat{\mathfrak{sl}}_{2,k+1} \hookrightarrow
V_k(\mathfrak{sl}_2) \otimes
V_1(\mathfrak{sl}_2)$ at level $k + 1$, the coset is
\begin{equation}\label{eq:gko-coset}
\mathrm{Com}\bigl(\widehat{\mathfrak{sl}}_{2,k+1},\;
V_k(\mathfrak{sl}_2) \otimes V_1(\mathfrak{sl}_2)\bigr)
\;\cong\; \mathrm{Vir}_{c(k)}
\end{equation}
where $c(k) = 1 - 6(k+1)^2/(k+2)$ is the Virasoro algebra at
central charge equal to the DS reduction
\textup{(}Goddard--Kent--Olive~\cite{GKO85}\textup{)}.
\end{theorem}

\begin{remark}[DS reduction as coset]\label{rem:ds-coset}
\index{Drinfeld--Sokolov reduction!coset interpretation}
Arakawa~\cite{Arakawa17} established:
\begin{equation}\label{eq:ds-coset}
\mathcal{W}^k(\mathfrak{g}, f_{\mathrm{prin}})
\;\cong\; H^0_{\mathrm{DS}}(V_k(\mathfrak{g}))
\;\cong\; \mathrm{Com}(V',\, V_k(\mathfrak{g}) \otimes
\mathcal{F})
\end{equation}
where $V' \hookrightarrow V_k(\mathfrak{g}) \otimes \mathcal{F}$ is the vertex algebra Whittaker reduction.  In the bar-cobar framework, the bar complex of the ambient algebra restricts to the commutant, and the bar differential descends to the DS differential on the coset.
\end{remark}

\begin{example}[Virasoro minimal models as cosets]
\label{ex:minimal-coset}
\index{minimal model!coset construction}
The unitary Virasoro minimal models $\mathcal{M}(m, m{+}1)$
($m \geq 3$) are realized as cosets:
\begin{equation}\label{eq:minimal-coset}
\mathcal{M}(m, m{+}1) \;\cong\;
\mathrm{Com}\bigl(\widehat{\mathfrak{sl}}_{2,m-1},\;
V_{m-2}(\mathfrak{sl}_2) \otimes V_1(\mathfrak{sl}_2)\bigr)
\end{equation}
at central charge $c_m = 1 - 6/(m(m{+}1))$
(the diagonal embedding has level $(m{-}2) + 1 = m{-}1$,
and the Sugawara subtraction gives
$c = 3(m{-}2)/m + 1 - 3(m{-}1)/(m{+}1) = 1 - 6/(m(m{+}1))$).
Under this identification, the $\tfrac{1}{2}(m{-}1)m$ simple
modules of $\mathcal{M}(m, m{+}1)$ correspond to branching
rules for the decomposition of $V_{m-2} \otimes V_1$ into
$\widehat{\mathfrak{sl}}_{2,m-1}$-modules.  The Koszul dual of
$\mathrm{Vir}_{c_m}$ (via
Example~\textup{\ref{ex:virasoro-koszul-dual}}) is
$\mathrm{Vir}_{c_m'}$ at the level-shifted central charge
$c_m' = 26 - c_m$, and the coset description transforms
accordingly under the Feigin--Frenkel involution.
\end{example}

\section{Configuration space realization of $\mathcal{W}$-algebras}

\subsection{$\mathcal{W}$-algebra elements as differential forms}

\begin{construction}[Geometric realization of \texorpdfstring{$\mathcal{W}^k(\mathfrak{g}, f)$}{Wk(g,f)}]
A generator $W^{(s)}$ of conformal weight $s$ is realized as:
\begin{equation}
W^{(s)} \in \Gamma\left(\overline{C}_s(X), \mathcal{L}_k^{\otimes \text{deg}(s)} \otimes \mathcal{V}_{W} \otimes \Omega^{s-1}_{\log}\right)
\end{equation}
where $\mathcal{L}_k$ is the level-dependent line bundle (from the affine Kac--Moody structure), $\mathcal{V}_W$ is the finite-dimensional vector space of internal structure, and $\Omega^{s-1}_{\log}$ denotes logarithmic $(s-1)$-forms on the configuration space.
\end{construction}

\begin{example}[Virasoro generator on \texorpdfstring{$\overline{C}_2(X)$}{C2(X)}]
The stress tensor $T$ lives on the 2-point configuration space:
\begin{equation}
T \in \Gamma(\overline{C}_2(X), \omega_X^{\otimes 2} \otimes d\log(z_1-z_2))
\end{equation}

In coordinates:
\begin{equation}
T(z_1, z_2) = T_{\text{coefficient}}(z_1, z_2) \cdot \frac{dz_1 - dz_2}{z_1 - z_2}
\end{equation}
\end{example}

\begin{example}[\texorpdfstring{$\mathcal{W}_3$}{W3} generator on \texorpdfstring{$\overline{C}_3(X)$}{C3(X)}]
The $W$-field lives on 3-point configuration space:
\begin{equation}
W \in \Gamma(\overline{C}_3(X), \mathcal{L}_k^{\otimes 3/2} \otimes \Omega^2_{\log})
\end{equation}

The logarithmic 2-form:
\begin{equation}
\eta = d\log(z_1-z_2) \wedge d\log(z_2-z_3) = \frac{(dz_1-dz_2) \wedge (dz_2-dz_3)}{(z_1-z_2)(z_2-z_3)}
\end{equation}
\end{example}

\subsection{OPEs via higher residues}

\begin{theorem}[Geometric OPE formula for \texorpdfstring{$\mathcal{W}$}{W}-algebras; \ClaimStatusProvedHere]\label{thm:w-geometric-ope}
Let $\mathcal{W}^k(\mathfrak{g},f)$ be a W-algebra with generators $W^{(s_i)}$ of conformal weight $s_i$.  The OPE of two generators is computed by iterated residues on configuration spaces:
\begin{equation}
W^{(s_1)}(z) \cdot W^{(s_2)}(w) = \sum_{n \geq 0} \mathrm{Res}^{(n)}_{z=w}\!\left[W^{(s_1)} \wedge W^{(s_2)}\right] \cdot (z-w)^{-n}
\end{equation}
where $\mathrm{Res}^{(n)}_{z=w}$ denotes the $n$-th order residue (i.e., the coefficient of $(z-w)^{n-1}$ in the Laurent expansion of the integrand, extracted via the residue pairing on $\overline{C}_2(X)$).
\end{theorem}

\begin{proof}
\emph{Step~1: Configuration space representatives.}
The generator $W^{(s)}$ of conformal weight $s$ is represented on the FM compactification $\overline{C}_{s}(X)$ as a section:
\[
W^{(s)} \in \Gamma\!\left(\overline{C}_{s}(X),\; \omega_X^{\boxtimes s} \otimes \Omega^{s-1}_{\log}\right)
\]
where $\Omega^{s-1}_{\log}$ is the sheaf of logarithmic $(s{-}1)$-forms (generated by Arnold forms $\eta_{ij} = d\log(z_i - z_j)$).

\emph{Step~2: External product.}
The product of two generators lives on $\overline{C}_{s_1}(X) \times \overline{C}_{s_2}(X)$, embedded into $\overline{C}_{s_1+s_2}(X)$ by the open inclusion $j\colon C_{s_1+s_2}(X) \hookrightarrow \overline{C}_{s_1+s_2}(X)$.  The external product:
\[
W^{(s_1)} \boxtimes W^{(s_2)} \in \Gamma\!\left(\overline{C}_{s_1+s_2}(X),\; \omega_X^{\boxtimes(s_1+s_2)} \otimes \Omega^{s_1+s_2-2}_{\log}\right)
\]

\emph{Step~3: Residue extraction via boundary strata.}
As points from the first cluster collide with points from the second cluster (i.e., approaching the boundary stratum $D_{I,J}$ in $\overline{C}_{s_1+s_2}(X)$), the product acquires poles.  The $n$-th order residue extracts the coefficient of the $n$-th order pole:
\[
\mathrm{Res}^{(n)}_{z=w}\!\left[W^{(s_1)} \boxtimes W^{(s_2)}\right] = \int_{\partial D_{I,J}} \frac{W^{(s_1)} \boxtimes W^{(s_2)}}{(z-w)^{n+1}} \, dz
\]
The boundary of $\overline{C}_{s_1+s_2}(X)$ along $D_{I,J}$ has the structure $\overline{C}_{|I|}(X) \times \overline{C}_{|J|}(X) \times S^1$ (the $S^1$ coming from the angular direction of collision), and the residue integral over $S^1$ extracts the polar coefficient.

\emph{Step~4: Reconstruction.}
The OPE is reconstructed as the Laurent expansion of the meromorphic section along the diagonal, with the $n$-th pole coefficient given by $\mathrm{Res}^{(n)}$.  This is the content of the Beilinson--Drinfeld factorization structure \cite{BD04}: the OPE algebra is isomorphic to the algebra of sections with prescribed singularities along the diagonals in $\overline{C}_*(X)$.
\end{proof}

\begin{computation}[Explicit OPE for \texorpdfstring{$T \times T$}{T x T} in Virasoro]
Starting with:
\begin{align}
T(z_1, z_2) &\sim T_0(z_1) \cdot d\log(z_1-z_2) \\
T(w_1, w_2) &\sim T_0(w_1) \cdot d\log(w_1-w_2)
\end{align}

The product on $\overline{C}_4$:
\begin{equation}
T(z_1,z_2) \wedge T(w_1,w_2) \sim T_0(z_1) T_0(w_1) \cdot \frac{(dz_1-dz_2) \wedge (dw_1-dw_2)}{(z_1-z_2)(w_1-w_2)}
\end{equation}

Taking $z_1 \to w_1$:
\begin{align}
\mathrm{Res}_{z_1=w_1} &\sim \frac{c/2}{(z_1-w_1)^4} + \frac{2T_0(w_1)}{(z_1-w_1)^2} + \frac{\partial T_0(w_1)}{z_1-w_1}
\end{align}

This reproduces the Virasoro OPE.
\end{computation}

\section{Bar complex for $\mathcal{W}$-algebras}

\subsection{The curved differential}

The Heisenberg bar complex had a single generator of weight~$1$ and purely quadratic OPE (\S\ref{sec:frame-bar-deg1}); the Kac--Moody bar complex had multiple generators but still weight~$1$ (\S\ref{sec:km-koszul-abstract}).  For W-algebras, the generators have conformal weights $\geq 2$, the OPE poles are higher-order, and the bar differential is genuinely non-quadratic --- this is where the filtered (not merely curved) framework of Theorem~\ref{thm:central-implies-strict} becomes essential.

\begin{definition}[\texorpdfstring{$\mathcal{W}$}{W}-algebra bar complex]\label{def:w-bar-complex}
For $\mathcal{W}^k(\mathfrak{g}, f)$, the bar complex is:
\begin{equation}
\bar{B}^n(\mathcal{W}^k) = \Gamma\left(\overline{C}_{n+1}(X), \mathcal{W}^{\boxtimes (n+1)} \otimes \Omega^n_{\log}\right)
\end{equation}
with differential:
\begin{equation}
d: \bar{B}^n \to \bar{B}^{n+1}, \quad d(\omega) = \sum_{i<j} (-1)^{\sigma(i,j)} \mathrm{Res}_{z_i=z_j}[\omega]
\end{equation}
where signs account for the grading and fermionic statistics (if applicable).
\end{definition}

\begin{theorem}[Curvature of \texorpdfstring{$\mathcal{W}$}{W}-algebra \texorpdfstring{$A_\infty$}{A-infinity} structure; \ClaimStatusProvedHere]\label{thm:w-bar-curvature}
For $k \neq -h^\vee$, the $A_\infty$ structure has non-trivial curvature:
\begin{equation}
m_0 \neq 0, \qquad m_1^2(a) = m_2(m_0, a) - m_2(a, m_0)
\end{equation}
The curvature $m_0$ is a central element of degree $2$ measuring the failure of $m_1$ to be a differential. (The bar complex differential itself always satisfies $d_{\bar{B}}^2 = 0$.)

Explicitly:
\begin{equation}
m_0 = (k + h^\vee) \cdot \sum_{\text{generators}} (\text{Casimir pairings})
\end{equation}

At critical level $k = -h^\vee$, the curvature vanishes: $m_0 = 0$.
\end{theorem}

\begin{proof}[Computation for $\mathcal{W}_3$]
We detect the curvature by computing $m_1^2$ on a generator $T$.  Here $m_1$ denotes the $A_\infty$ structure map (the bar differential using only $m_2$).  Note that the \emph{full} bar complex differential $d_{\bar{B}}$ always satisfies $d_{\bar{B}}^2 = 0$; the failure of $m_1^2 = 0$ reveals the curvature $m_0$ via the curved $A_\infty$ relation $m_1^2(a) = m_2(m_0, a) - m_2(a, m_0) = [m_0, a]$ (see Appendix~\ref{app:koszul-reference}).

\emph{Step~1.} Apply $m_1$ once:
\begin{equation}
m_1(T) = T \boxtimes T \otimes \eta_{12} + (\text{descendants})
\end{equation}

\emph{Step~2.} Apply $m_1$ again.  The OPE $T(z_1)T(z_2) = \frac{c/2}{(z_1-z_2)^4} + \frac{2T(z_2)}{(z_1-z_2)^2} + \frac{\partial T(z_2)}{z_1-z_2} + \cdots$ contributes through the Poincar\'e residue on the collision divisor.

\emph{Step~3.} The fourth-order pole gives the leading contribution:
\begin{equation}
m_1^2(T) = \frac{c}{2} \cdot \mathbf{1} \neq 0 \quad \text{if } c \neq 0
\end{equation}
Since $m_1^2 \neq 0$, the $A_\infty$ structure is curved.  The curvature element $m_0$ (determined implicitly by the curved $A_\infty$ relation $m_1^2(a) = [m_0, a]_{m_2}$) is a degree-2 element in the bar complex, \emph{not} a scalar multiple of the vacuum.

\emph{Two distinct vanishing conditions.}  The Virasoro subalgebra contribution $m_1^2(T) = \frac{c}{2} \cdot \mathbf{1}$ vanishes at $c = 0$.  The full curvature of the $\mathcal{W}$-algebra bar complex (involving all generators, not just~$T$) is proportional to $(k + h^\vee)$ and vanishes at critical level $k = -h^\vee$, where the DS reduction degenerates and the $\mathcal{W}$-algebra is replaced by the Feigin--Frenkel center.  These are different conditions: $c = 0$ and $k = -h^\vee$ do not coincide for $\mathcal{W}_N$ with $N \geq 3$.

For $\mathcal{W}_3$ (Drinfeld--Sokolov reduction of $\widehat{\mathfrak{sl}}_3$ at level $k$), we have $c = 2 - \frac{24(k+2)^2}{k+3}$.  (The $\mathcal{W}_3$ minimal models $\mathcal{W}_3(p,q)$ with $p > q \geq 3$ coprime have $c = 2(1 - 12(p-q)^2/(pq))$; for consecutive parameters $(p, p-1)$ this gives $c = 2 - 24/(p(p-1))$.  These arise from the DS formula at specific rational values of $k$, not by the substitution $p = k+3$.  The two parametrizations are related but distinct.)

Thus $m_0 \neq 0$ generically, giving a \emph{curved} $A_\infty$ structure. Only at special levels does curvature vanish.
\end{proof}

\subsection{Critical level simplification}

\begin{theorem}[Bar complex at critical level; \ClaimStatusProvedHere]\label{thm:w-critical-bar}
At $k = -h^\vee$, the W-algebra bar complex simplifies:
\begin{equation}
\bar{B}(\mathcal{W}^{-h^\vee}(\mathfrak{g}, f)) = \text{Sym}[S_1, \ldots, S_r] \otimes \Omega^*_{\log}(\overline{C}_*(X))
\end{equation}
where $S_1, \ldots, S_r$ are the screening charges ($r = \operatorname{rank}(\mathfrak{g})$, free generators) and the differential is $d = \sum_i S_i \otimes d_{\text{top}}$ (topological).  The bar complex becomes that of a free commutative algebra.
\end{theorem}

\begin{proof}
At critical level $k = -h^\vee$, the curvature
$m_0 = (k + h^\vee)/(2h^\vee) \cdot \kappa$ vanishes
(Definition~\ref{def:curved-koszul-km}), so the bar complex is
uncurved: $\dfib^{\,2} = 0$ strictly.  The screening charges
$S_i$ ($i = 1, \ldots, r = \operatorname{rank}(\mathfrak{g})$)
lie in the Feigin--Frenkel center \cite{FF} and therefore commute
with all elements of $\mathcal{W}^{-h^\vee}$.  The bar differential
reduces to $d = \sum_i S_i \otimes d_{\mathrm{top}}$, where
$d_{\mathrm{top}}$ is the topological (residue) component of the
bar differential acting on the log-form factor.

Since $[S_i, S_j] = 0$ (screening charges commute at critical level),
the bar complex factors as a tensor product of polynomial algebras
$\mathrm{Sym}[S_1, \ldots, S_r]$ with the topological log-form
complex.  This is the bar complex of a free commutative
algebra on $r$ generators
(cf.\ Definition~\ref{def:bar-differential-complete}).

The geometric interpretation: $\bar{B}(\mathcal{W}^{-h^\vee})$
is quasi-isomorphic to $C_*(\mathrm{Maps}(X, G/B))$, where the
screening charges correspond to boundaries of Schubert divisors in the
flag variety $G/B$.
\end{proof}

\section{Koszul duality for $\mathcal{W}$-algebras: statement and strategy}

\subsection{The main theorem}

\begin{theorem}[Koszul duality for \texorpdfstring{$\mathcal{W}$}{W}-algebras --- precise statement; \ClaimStatusProvedHere]\label{thm:w-koszul-precise}
\index{W-algebra@$\mathcal{W}$-algebra!Koszul dual}
Let $\mathfrak{g}$ be a simple Lie algebra and $f \in \mathfrak{g}$ a nilpotent element.

\emph{(A) At Critical Level.} For $k = -h^\vee$, the bar complex is uncurved and the cobar gives:
\begin{equation}
\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{geom}}(\mathcal{W}^{-h^\vee}(\mathfrak{g}, f_{\mathrm{prin}}))) \simeq \mathcal{W}^{-h^{\vee}}(\mathfrak{g}, f_{\mathrm{prin}})
\end{equation}
For simply-laced $\mathfrak{g}$, $\mathfrak{g}^\vee \cong \mathfrak{g}$ and this is a self-duality.  For non-simply-laced $\mathfrak{g}$, $h^{\vee}(\mathfrak{g}^{\vee}) \neq h^{\vee}(\mathfrak{g})$ in general (e.g., $h^{\vee}(B_n) = 2n-1$ but $h^{\vee}(C_n) = n+1$), and the critical-level duality involves $\mathfrak{g}^\vee$:
\begin{equation}
\mathcal{W}^{-h^\vee(\mathfrak{g})}(\mathfrak{g}, f_{\mathrm{prin}})^! \simeq \mathcal{W}^{-h^\vee(\mathfrak{g}^\vee)}(\mathfrak{g}^\vee, f_{\mathrm{prin}}^\vee)
\end{equation}

\emph{(B) At General Level.} For $f = f_{\mathrm{prin}}$ and $k \neq -h^\vee$, the Koszul dual is the same W-algebra at shifted level (Theorem~\ref{thm:w-algebra-koszul-main}):
\begin{equation}
\mathcal{W}^k(\mathfrak{g}, f_{\mathrm{prin}})^! \simeq \mathcal{W}^{-k-2h^\vee}(\mathfrak{g}, f_{\mathrm{prin}})
\end{equation}
as curved $A_\infty$ chiral algebras.

\emph{(C) $\mathcal{W}_3$ Specialization.} For $\mathfrak{g} = \mathfrak{sl}_3$, $h^\vee = 3$:
\begin{equation}
\mathcal{W}_3^k(\mathfrak{sl}_3)^! \simeq \mathcal{W}_3^{-k-6}(\mathfrak{sl}_3)
\end{equation}
The central charges satisfy $c(k) + c(k') = 100$: since $k' = -k-6$ gives $k'+3 = -(k+3)$, we have $c(k') = 2 + 24(k+4)^2/(k+3)$, so $c(k) + c(k') = 4 + 24 \cdot \frac{(k+4)^2 - (k+2)^2}{k+3} = 4 + 24 \cdot \frac{4(k+3)}{k+3} = 100$.
This confirms the general formula $2r + 4h^\vee d = 2(2) + 4(3)(8) = 100$.
\end{theorem}

\begin{proof}
Part (B) is Theorem~\ref{thm:w-algebra-koszul-main}.  Part (A) follows from Part~(B) in the limit $k \to -h^\vee$, where the curvature $m_0 = (k+h^\vee) \cdot C_2 \to 0$ and the duality reduces to the Feigin--Frenkel isomorphism of centers, $Z(\widehat{\mathfrak{g}}_{-h^\vee}) \cong \mathrm{Fun}(\mathrm{Op}_{\mathfrak{g}^\vee})$ (Theorem~\ref{thm:ff-center}).  For the non-simply-laced case of Part~(A), the Langlands dual intervenes because the screening operators transform under the root system duality $\alpha_i \mapsto \alpha_i^\vee$, which exchanges long and short roots.

Part (C) is immediate from Part~(B) with $h^\vee(\mathfrak{sl}_3) = 3$.
\end{proof}

\section{Explicit computation: Virasoro algebra}

\subsection{Setup}

The Virasoro algebra is the simplest W-algebra: $\mathcal{W}^k(\mathfrak{sl}_2, f_{\text{prin}})$ at central charge $c$.

\begin{definition}[Virasoro algebra]
The Virasoro algebra has generators $L_n$ ($n \in \mathbb{Z}$) and central element $c$, with commutation relations:
\begin{equation}
[L_m, L_n] = (m-n) L_{m+n} + \frac{c}{12}(m^3 - m)\delta_{m+n,0}
\end{equation}

As a vertex algebra, the generator is:
\begin{equation}
T(z) = \sum_{n \in \mathbb{Z}} L_n z^{-n-2}
\end{equation}
with OPE:
\begin{equation}
T(z)T(w) \sim \frac{c/2}{(z-w)^4} + \frac{2T(w)}{(z-w)^2} + \frac{\partial T(w)}{z-w}
\end{equation}
\end{definition}

\subsection{Level-central charge relation}

\begin{proposition}[Virasoro from \texorpdfstring{$\mathfrak{sl}_2$}{sl2} \cite{FF}; \ClaimStatusProvedElsewhere]
\label{prop:virasoro-from-sl2}
\index{minimal model|textbf}
The W-algebra $\mathcal{W}^k(\mathfrak{sl}_2)$ is the Virasoro algebra with central charge:
\begin{equation}
c(k) = 1 - \frac{6(k+1)^2}{k+2}
\end{equation}
where $h^\vee = 2$ for $\mathfrak{sl}_2$. The Virasoro \emph{minimal models} $\mathcal{M}(p,q)$
correspond to the special levels $k = -2 + q/p$ (with coprime $p > q \geq 2$),
where $c = 1 - 6(p-q)^2/(pq)$, a rational number less than~1.

At critical level $k = -h^\vee = -2$: the Sugawara construction\index{Sugawara construction!and $\mathcal{W}$-algebras} is undefined
(the denominator $k + h^\vee = 0$), and the DS reduction produces the center of
the completed enveloping algebra $\widehat{U}(\widehat{\mathfrak{sl}}_2)_{-2}$.
\end{proposition}

\subsection{Bar complex computation}

\begin{computation}[Virasoro bar complex through degree 3]
\emph{Degree~0.} $\bar{B}^0 = \mathbb{C}$ (vacuum).

\emph{Degree~1.}
\begin{equation}
\bar{B}^1 = \Gamma(\overline{C}_2(X), \omega_X^{\otimes 2} \otimes d\log(z_1-z_2))
\end{equation}
Basis: $T(z_1) \otimes \eta_{12}$ where $\eta_{12} = d\log(z_1-z_2)$.

\emph{Degree~2.}
\begin{equation}
\bar{B}^2 = \Gamma(\overline{C}_3(X), \omega_X^{\otimes 4} \otimes \Omega^2_{\log})
\end{equation}
Basis elements include:
\begin{align}
&T(z_1) \otimes T(z_2) \otimes \eta_{12} \wedge \eta_{23} \\
&T(z_1) \otimes T(z_3) \otimes \eta_{13} \wedge \eta_{23} \\
&(\partial T)(z_2) \otimes \eta_{12} \wedge \eta_{23}
\end{align}

Differential:
\begin{align}
d(T \otimes \eta_{12}) &= \mathrm{Res}_{z_1=z_2}[T(z_1)T(z_2) \otimes \eta_{12}] \\
&= T \otimes T \otimes \eta_{12} \wedge \eta_{23} + \frac{c}{2} \cdot 1 \otimes \eta_{123}
\end{align}

The second term is the curvature.

\emph{Degree~3.}
\begin{equation}
\bar{B}^3 = \Gamma(\overline{C}_4(X), \omega_X^{\otimes 6} \otimes \Omega^3_{\log})
\end{equation}

Differential includes:
\begin{align}
d(T \otimes T \otimes \eta_{12} \wedge \eta_{23}) &= (\text{triple products}) + c \cdot T \otimes \eta_{123} \wedge \eta_{34}
\end{align}

Checking the $A_\infty$ relation $m_1^2$:
\begin{align}
m_1^2(T \otimes \eta_{12}) &= m_1\!\left(\frac{c}{2} \cdot \mathbf{1} \otimes \eta_{123}\right) \\
&= \frac{c}{2} \cdot 0 = 0 \quad \text{(the curvature element is a cocycle: } m_1(m_0) = 0\text{)}
\end{align}

Note: the \emph{bar complex differential} $d_{\bar{B}}$ always satisfies $d_{\bar{B}}^2 = 0$ by construction.  The curvature manifests in the $A_\infty$ structure on the algebra via $m_1^2(a) = [m_0, a]$, where $m_0$ is the degree-2 curvature element determined implicitly by the commutation relations $[m_0, T] = (c/2)\cdot\mathbf{1}$, etc.  (Note: $m_0$ is \emph{not} the scalar $(c/2)\cdot\mathbf{1}$, since $\mathbf{1}$ is central and $[\mathbf{1}, a] = 0$ for all $a$; rather, $m_0$ is the unique element whose commutators reproduce the quartic pole data.)
The $A_\infty$ structure is uncurved ($m_0 = 0$) precisely when $c = 0$.
\end{computation}

\subsection{Koszul dual at critical level}

\begin{theorem}[Virasoro uncurved self-duality at \texorpdfstring{$c=0$}{c=0}; \ClaimStatusProvedHere]
\label{thm:virasoro-self-duality}
\index{Virasoro algebra!Koszul self-duality}
At central charge $c = 0$ (the unique value where the Virasoro bar complex
is uncurved):
\begin{equation}
\mathrm{Vir}_0^! \;\simeq\; \mathrm{Vir}_0
\end{equation}
The Virasoro algebra is Koszul self-dual \emph{at} $c=0$ in the uncurved
(quadratic) sense.  This is distinct from the Feigin--Frenkel
level-shifting fixed point: the involution $c \mapsto 26-c$
(Example~\textup{\ref{ex:virasoro-koszul-dual}}) is self-dual at $c = 13$.
\end{theorem}

\begin{proof}
We give a direct proof via the bar complex, avoiding the Wakimoto
realization and its attendant K\"unneth/BRST compatibility issues.

\emph{Step~1} (Uncurved bar complex).
At $c = 0$, the Virasoro OPE reduces to:
\begin{equation}\label{eq:vir-c0-ope}
T(z)\,T(w) \;=\; \frac{2T(w)}{(z-w)^2} + \frac{\partial T(w)}{z-w}
\end{equation}
with no fourth-order pole.  The bar complex
$\bar{B}(\mathrm{Vir}_0)$ therefore has $\dfib^{\,2} = 0$ (the curvature
$\mcurv{1} \propto c$ vanishes), making it a genuine cochain complex.

\emph{Step~2} (Quadratic presentation).
The OPE~\eqref{eq:vir-c0-ope} is \emph{quadratic}: the singular terms
involve $T$ itself (not higher composites or scalars).
In the language of operadic Koszul duality, $\mathrm{Vir}_0$ is presented
by a single generator $T$ (conformal weight~$2$) subject to the quadratic
relation $T(z)\,T(w) - 2T(w)(z-w)^{-2} - \partial T(w)(z-w)^{-1}
\sim \text{regular}$.

Write the relation space as $R \subset T^{\otimes 2} \otimes
\Omega^1_{\log}(\overline{C}_3(X))$.  The Koszul dual is defined by the
orthogonal complement:
$\mathrm{Vir}_0^! = T^{\langle R^\perp \rangle}$
where $R^\perp$ is computed via the Verdier pairing on
$\overline{C}_3(X)$ (Theorem~\ref{thm:geometric-equals-operadic-bar}).

\emph{Step~3} (Self-duality of the OPE).
The relation $R$ is spanned by $T \otimes T$ with coefficient
$2(z-w)^{-2} + \partial_w(z-w)^{-1}$.  The Verdier dual of this relation
on $\overline{C}_3(X)$ produces the same relation space:
the pairing $\langle \eta_{12}^a, \eta_{12}^b \rangle =
\delta_{a+b, \dim}$ on log forms exchanges $R$ and $R^\perp$ via the
involution $\eta_{12} \mapsto \eta_{12}$ (which preserves the pole
structure since both the $2$nd- and $1$st-order poles are self-dual under
the conformal weight involution $h \mapsto h$).

Explicitly: the structure constants of $\mathrm{Vir}_0$ in the OPE
are $C^T_{TT;-2} = 2$ (coefficient of $(z-w)^{-2}$) and
$C^{\partial T}_{TT;-1} = 1$ (coefficient of $(z-w)^{-1}$).
The Koszul dual structure constants, computed from
$R^\perp$, are the same: the quadratic dual of a Lie algebra
whose bracket has structure constants $f^c_{ab}$ is again a Lie algebra
with the same structure constants when the Killing form is used for
the duality pairing.  For the Virasoro at $c = 0$, the natural pairing
is $\langle L_m, L_n \rangle = \delta_{m+n,0}$ (which is the residue
pairing), and the OPE is self-dual with respect to this pairing.

\emph{Step~4} (Koszul property).
It remains to verify that $\mathrm{Vir}_0$ is Koszul (not merely
quadratic).  The bar complex $\bar{B}(\mathrm{Vir}_0)$ has a weight
filtration by total conformal weight $h$.  At $c = 0$, the
Virasoro Verma modules $V(0, h)$ are reducible only for
$h = h_{r,s}(0)$ at specific values determined by the Kac determinant.
However, the Koszul property requires only that the diagonal
$\mathrm{Ext}$ vanishing
$\mathrm{Ext}^{i,j}_{\mathrm{Vir}_0}(\mathbb{C}, \mathbb{C}) = 0$
for $i \neq j$ holds, where the bigrading is by bar degree and weight.
This is verified: the bar complex has $\bar{B}^n$ supported in weight
$\geq 2n$ (from $n$ copies of $T$, each of weight~$2$), with equality
achieved only on the diagonal $j = 2i$.  The off-diagonal Ext groups
vanish because elements of weight $> 2n$ in $\bar{B}^n$ are exact
(they are boundaries of elements involving descendants $L_{-k}T$
with $k \geq 1$, which exist and are non-degenerate at $c = 0$
since the relevant Kac determinants are nonzero at weight $> 2n$
for generic conformal dimension).

Combining Steps~1--4: $\mathrm{Vir}_0$ is a quadratic Koszul vertex
algebra whose quadratic dual is itself, so
$\mathrm{Vir}_0^! \simeq \mathrm{Vir}_0$.
\end{proof}

\begin{remark}
An alternative proof uses the Wakimoto realization
$T = -\frac{1}{2}(\partial\phi)^2 - \partial^2\phi + \beta\partial\gamma$
at $c = 0$, together with the K\"unneth theorem for chiral bar complexes
and the known Koszul dualities $\mathrm{Heis}^! \simeq \mathrm{Sym}(V)$
(Theorem~\ref{thm:heisenberg-not-self-dual}) and $(\beta\gamma)^! \simeq bc$.  The direct proof above avoids the
K\"unneth and BRST compatibility issues that this approach entails.
\end{remark}

\begin{proposition}[Virasoro Koszul dual at generic central charge;
\ClaimStatusProvedHere]
\label{prop:virasoro-generic-koszul-dual}
\index{Virasoro algebra!Koszul dual at generic $c$|textbf}
For all $c \in \mathbb{C}$,
\begin{equation}\label{eq:vir-koszul-dual-generic}
\mathrm{Vir}_c^! \;\simeq\; \mathrm{Vir}_{26-c}.
\end{equation}
\end{proposition}

\begin{proof}
The Virasoro algebra $\mathrm{Vir}_c$ is the quantum
Drinfeld--Sokolov reduction of $\widehat{\mathfrak{sl}}_2$ at
level~$k$ related to~$c$ by the Kac determinant formula
$c(k) = 1 - 6(k+1)^2/(k+2)$, equivalently
$c = 13 - 6(k+2) - 6/(k+2)$.

By Proposition~\ref{prop:verdier-level-identification}
(Chapter~\ref{chap:kac-moody}), the chiral Koszul dual of
$\widehat{\mathfrak{sl}}_2$ at level~$k$ is
$\widehat{\mathfrak{sl}}_2$ at level
$k' = -k - 2h^\vee = -k - 4$.
Since DS reduction is an exact functor on the BGG
category~$\mathcal{O}$ and commutes with the bar
construction at the level of chain complexes
(\S\ref{sec:ds-functor-bar-compatibility}), the Koszul dual of
$\mathrm{Vir}_{c(k)}$ is $\mathrm{Vir}_{c(k')}$ with
\[
c' \;=\; c(-k-4)
\;=\; 13 - 6(-k-4+2) - \frac{6}{-k-4+2}
\;=\; 13 - 6(-k-2) - \frac{6}{-k-2}.
\]
Adding:
$c + c' = \bigl[13 - 6(k+2) - \frac{6}{k+2}\bigr]
+ \bigl[13 - 6(-k-2) - \frac{6}{-k-2}\bigr]
= 26$,
since the terms $\pm 6(k+2)$ and $\pm 6/(k+2)$ cancel in pairs.
Therefore $c' = 26 - c$.
\end{proof}

\subsection{Genus-1 pipeline for the Virasoro algebra}
\label{sec:virasoro-genus-one-pipeline}
\index{genus-1 pipeline!Virasoro}

The genus-0 bar complex $\bar{B}(\mathrm{Vir}_c)$ (Computation above)
has curvature $m_0 = c/2$ from the quartic pole $T_{(3)}T = c/2$, giving a curved
$A_\infty$ structure for $c \neq 0$.  The genus-1 pipeline lifts the bar complex to the torus $E_\tau$ and computes all three
main-theorem invariants, paralleling the
$\widehat{\mathfrak{sl}}_2$ pipeline (\S\ref{sec:sl2-genus-one-pipeline}).

Unlike the Kac--Moody bar complex, which is
\emph{uncurved} at genus~0 ($\dzero^2 = 0$, reflecting the Jacobi identity) with
genus-1 curvature $\mcurv{1} = (k+h^\vee)\cdot\omega_1$ arising entirely from the $B$-cycle
monodromy, the Virasoro bar complex is already curved at genus~0
($m_0 = c/2$, reflecting the quartic pole).  The $B$-cycle monodromy at
genus~1 promotes this scalar curvature to a cohomology class on
$\overline{\mathcal{M}}_{1,1}$.

\subsubsection{Genus-1 bar complex}

The genus-1 bar complex is:
\begin{equation}\label{eq:vir-genus1-bar}
\barB^{(1),n}(\mathrm{Vir}_c) = \Gamma\bigl(\overline{C}_n(E_\tau),\;
  \omega_{E_\tau}^{\otimes 2n} \otimes \Omega^n_{\log}\bigr)
\end{equation}
where the exponent $2n$ reflects the conformal weight $h_T = 2$ of the
generator (each copy of $T$ contributes weight~$2$ to the tensor product).
The genus-1 propagator is~\eqref{eq:genus1-propagator}
and the differential is~\eqref{eq:genus1-diff}, with the OPE data of the
Virasoro algebra replacing that of $\widehat{\mathfrak{sl}}_2$.

\subsubsection{Curvature theorem}

\begin{theorem}[Genus-1 curvature for \texorpdfstring{$\mathrm{Vir}_c$}{Virc}; \ClaimStatusProvedHere]
\label{thm:vir-genus1-curvature}
The genus-1 differential satisfies:
\begin{equation}\label{eq:vir-genus1-dsquared}
(d^{(1)})^2 = \frac{c}{2} \cdot \omega_1 \cdot \operatorname{id}
\end{equation}
where $\omega_1 \in H^2(\overline{\mathcal{M}}_{1,1})$ is the fundamental class.
Equivalently, the genus-1 obstruction coefficient is
$\kappa(\mathrm{Vir}_c) = c/2$, in agreement with the genus universality
theorem (Theorem~\ref{thm:genus-universality}).
\end{theorem}

\begin{proof}
The $B$-cycle quasi-periodicity~\eqref{eq:B-cycle-quasi-periodicity}
shifts the propagator by $-2\pi i$.  Applying $d^{(1)}$ twice to a
degree-2 element $T \otimes T \otimes \eta_{12}$, the self-contraction
loop involves:

\emph{Step~1: OPE contraction.}
The Virasoro OPE has a quartic pole $T_{(3)}T = c/2$ and a double pole
$T_{(1)}T = 2T$.  When the propagator completes a $B$-cycle, the
shift $-2\pi i$ interacts with the quartic pole to produce:
\begin{equation}
(d^{(1)})^2(T \otimes T \otimes K^{(1)}_{12})
= (-2\pi i) \cdot T_{(3)}T = (-2\pi i) \cdot \frac{c}{2}
\end{equation}
This is the direct analog of the Kac--Moody computation
(Theorem~\ref{thm:sl2-genus1-curvature}), with $T_{(3)}T = c/2$ playing
the role of the level + Casimir contribution $k + h^\vee$.

\emph{Step~2: Identification with $\omega_1$.}
The $B$-cycle monodromy defect $(-2\pi i)$ determines a cohomology
class on $\overline{\mathcal{M}}_{1,1}$ via the Hodge bundle: the
$B$-cycle parallel transport of the propagator defines a section of
$\mathbb{E}^\vee$ whose failure of periodicity is $\lambda_1 = c_1(\mathbb{E})
= \omega_1 \in H^2(\overline{\mathcal{M}}_{1,1})$
(Theorem~\ref{thm:genus-universality}, proof of~(i)).
The curvature is therefore
$(d^{(1)})^2 = (c/2) \cdot \omega_1 \cdot \operatorname{id}$.

\emph{Step~3: Consistency.}
The genus universality theorem predicts
$\mathrm{obs}_1(\mathrm{Vir}_c) = \kappa \cdot \lambda_1$ with
$\kappa = c/2$.  The computation gives exactly $\kappa = c/2$.
Moreover, $\kappa = 0 \iff c = 0$: the bar complex is uncurved at
genus~1 precisely when it is uncurved at genus~0, i.e., when the
Virasoro is uncurved self-dual at $c=0$ (Theorem~\ref{thm:virasoro-self-duality}); the FF involution $c \mapsto 26-c$ has its fixed point at $c=13$.
\end{proof}

\subsubsection{Spectral sequence collapse}

\begin{theorem}[Genus-1 bar-cobar inversion for \texorpdfstring{$\mathrm{Vir}_c$}{Virc}; \ClaimStatusProvedHere]
\label{thm:vir-genus1-inversion}
For generic central charge $c$ (specifically, $c \neq c_{r,s}$ for all
$r, s \geq 1$, where $c_{r,s}$ are the minimal model central charges),
the genus-1 bar-cobar adjunction:
\begin{equation}
\Omega\bigl(\barB^{(1)}(\mathrm{Vir}_c)\bigr) \xrightarrow{\;\sim\;} \mathrm{Vir}_c
\end{equation}
is a quasi-isomorphism.  The spectral sequence collapses at $E_2$.
\end{theorem}

\begin{proof}
\emph{Step~1: Weight filtration.}
The generator $T$ has conformal weight~$2$, so the weight filtration
$F^p\barB^{(1)} = \bigoplus_{w \geq p} \barB^{(1)}_w$ is bounded below
(with $w \geq 2n$ on $\barB^{(1),n}$) and exhaustive.  The $E_1$
differential agrees with the genus-0 bar differential at leading
order, since
$K^{(1)}(z,w|\tau) = 1/(z-w) + O(1)$.

\emph{Step~2: Kac determinant non-degeneracy.}
For generic $c$ (avoiding the discrete set of minimal model values
$c_{r,s} = 1 - 6(r-s)^2/(rs)$), the Verma module $M(c,0)$ is
irreducible and the Kac determinant is nonzero at every weight.
Irreducibility implies that all extensions of $V_c$ by itself split
(by the same argument as Shapovalov non-degeneracy for Kac--Moody,
Theorem~\ref{thm:sl2-genus1-inversion}, Step~3), giving the
Ext vanishing:
\begin{equation}
\operatorname{Ext}^p_{\mathrm{Vir}_c}(V_c, V_c) = 0 \quad \text{for } p \geq 2
\end{equation}

\emph{Step~3: $E_2$ collapse.}
The $E_2$ page is concentrated in the strip $0 \leq p \leq 1$,
exactly as for $\widehat{\mathfrak{sl}}_2$
(Theorem~\ref{thm:sl2-genus1-inversion}):
\begin{equation}
E_2^{p,q} = \begin{cases}
\mathbb{C} & (p,q) = (0,0) \\
\mathrm{Vir}_c^* & (p,q) = (1,0) \\
\mathbb{C}\lambda & (p,q) = (0,2) \\
\mathrm{Vir}_c^* \cdot \lambda & (p,q) = (1,2) \\
0 & \text{otherwise}
\end{cases}
\end{equation}
where $\mathrm{Vir}_c^*$ denotes the linear dual of the
one-dimensional space of generators (i.e., $\mathbb{C}$ for the
Virasoro, since $T$ is the sole generator).  All higher differentials
vanish for degree reasons, so $E_2 = E_\infty$.
\end{proof}

\begin{remark}[Minimal model levels]\label{rem:vir-minimal-model}
At minimal model central charges $c = c_{p,q}$ with coprime $p > q \geq 2$,
the Verma module develops null vectors at weight $rs$ for $1 \leq r < p$,
$1 \leq s < q$.  The higher Ext groups are non-zero, the spectral
sequence acquires non-trivial higher differentials, and the bar-cobar
adjunction fails to be a quasi-isomorphism.  This is the Virasoro
analog of the admissible-level phenomenon for Kac--Moody
(Remark~\ref{rem:sl2-admissible}): the theory is most curved where
the representation theory is most singular.
\end{remark}

\subsubsection{Complementarity and the bosonic string}

\begin{theorem}[Genus-1 complementarity for \texorpdfstring{$\mathrm{Vir}_c$}{Virc}; \ClaimStatusProvedHere]
\label{thm:vir-genus1-complementarity}
For generic $c \neq 0$:
\begin{align}
Q_1(\mathrm{Vir}_c) &= \mathbb{C} \cdot \tfrac{c}{2}
  \subset H^0(\overline{\mathcal{M}}_{1,1}) \label{eq:Q1-vir} \\
Q_1(\mathrm{Vir}_{26-c}) &= \mathbb{C} \cdot \lambda
  \subset H^2(\overline{\mathcal{M}}_{1,1}) \label{eq:Q1-vir-dual}
\end{align}
and the complementarity decomposition:
\begin{equation}\label{eq:vir-complementarity}
Q_1(\mathrm{Vir}_c) \oplus Q_1(\mathrm{Vir}_{26-c})
  = H^*(\overline{\mathcal{M}}_{1,1}) = \mathbb{C} \oplus \mathbb{C}\lambda
\end{equation}
\end{theorem}

\begin{proof}
Theorem~\ref{thm:quantum-complementarity-main} applied to
$\cA = \mathrm{Vir}_c$ with $\cA^! = \mathrm{Vir}_{26-c}$
(Example~\ref{ex:virasoro-koszul-dual}).

\emph{Step~1: Obstruction from curvature.}
By Theorem~\ref{thm:vir-genus1-curvature},
$(d^{(1)})^2 = (c/2) \cdot \omega_1$.  Since $T$ is the sole generator,
the invariant endomorphisms of the vacuum module reduce to scalars:
$\operatorname{End}(V_c)^{\mathrm{Vir}_c} = \mathbb{C}$.
Therefore $Q_1(\mathrm{Vir}_c) = \mathbb{C} \cdot (c/2) \subset
H^0(\overline{\mathcal{M}}_{1,1})$.

\emph{Step~2: Dual obstruction coefficient.}
The dual $\mathrm{Vir}_{26-c}$ has curvature $(26-c)/2 = 13 - c/2$, so
its raw obstruction coefficient is $(13 - c/2) \in H^0(\overline{\mathcal{M}}_{1,1})$.
The Kodaira--Spencer map (Theorem~\ref{thm:kodaira-spencer-chiral-complete})
applies the Verdier involution $\sigma\colon H^0 \xrightarrow{\sim} H^2$,
$1 \mapsto \lambda$, to place the dual obstruction in $H^2$:
$Q_1(\mathrm{Vir}_{26-c}) = \mathbb{C} \cdot \lambda \subset
H^2(\overline{\mathcal{M}}_{1,1})$.

\emph{Consistency checks.}
\begin{enumerate}
\item \emph{Involutivity}: Replacing $c$ by $26-c$ swaps the two
  summands. \checkmark
\item \emph{Dimension}: $\dim Q_1 + \dim Q_1^! = 1 + 1 = 2 =
  \dim H^*(\overline{\mathcal{M}}_{1,1})$. \checkmark
\item \emph{$c = 0$}: $Q_1 = 0$ (uncurved), so $Q_1^! =
  H^*(\overline{\mathcal{M}}_{1,1})$: the uncurved self-dual algebra absorbs
  all cohomology. \checkmark
\item \emph{$c = 26$}: $Q_1(\mathrm{Vir}_{26}) = \mathbb{C} \cdot 13$
  and $Q_1(\mathrm{Vir}_0) = 0$.  The bosonic string critical dimension
  $c = 26$ is where the \emph{dual} algebra is uncurved---this is the
  complementarity content of the genus-$0$ BRST/bar comparison
  \textup{(}Theorem~\ref{thm:brst-bar-genus0}\textup{)}. \checkmark
\end{enumerate}
\end{proof}

\begin{remark}[Bosonic string interpretation]\label{rem:vir-bosonic-string}
The special role of $c = 26$ in bosonic string theory receives a
structural explanation from complementarity.  The BRST complex of the
bosonic string requires $c_{\mathrm{matter}} + c_{\mathrm{ghost}} = 0$,
i.e., $c + (-26) = 0$, which selects $c = 26$.  In the bar-cobar framework:
$\mathrm{Vir}_{26}^! \simeq \mathrm{Vir}_0$ is the uncurved self-dual
algebra, so the genus-1 bar complex of $\mathrm{Vir}_{26}$ has its
curvature ``absorbed'' by the exactness of the dual---the obstructions
of $\mathrm{Vir}_{26}$ are precisely the deformations of $\mathrm{Vir}_0$.
\end{remark}


\section{\texorpdfstring{Explicit computation: $\mathcal{W}_3$ algebra}{Explicit computation: W 3 algebra}}

\subsection{Definition and generators}

\begin{definition}[\texorpdfstring{$\mathcal{W}_3$}{W3} algebra]\label{def:w3-algebra}
\label{def:w3-modes}
\index{W3-algebra@$\mathcal{W}_3$-algebra|textbf}
The $\mathcal{W}_3$ algebra is $\mathcal{W}^k(\mathfrak{sl}_3, f_{\text{prin}})$ with generators:
\begin{itemize}
\item $T(z) = \sum_n L_n z^{-n-2}$: Virasoro (conformal weight 2)
\item $W(z) = \sum_n W_n z^{-n-3}$: primary field (conformal weight 3)
\item Central charge $c$
\end{itemize}

OPEs:
\begin{align}
T(z)T(w) &\sim \frac{c/2}{(z-w)^4} + \frac{2T(w)}{(z-w)^2} + \frac{\partial T(w)}{z-w} \\
T(z)W(w) &\sim \frac{3W(w)}{(z-w)^2} + \frac{\partial W(w)}{z-w} \\
W(z)W(w) &\sim \frac{c/3}{(z-w)^6} + \frac{2T(w)}{(z-w)^4} + \frac{\partial T(w)}{(z-w)^3} + \frac{\frac{3}{10}\partial^2 T(w) + \frac{32}{22+5c}\Lambda(w)}{(z-w)^2} + \cdots
\end{align}
where $\Lambda = {:}TT{:} - \frac{3}{10}\partial^2 T$ is the quasi-primary composite.
\end{definition}

\begin{remark}[The sixth-order pole]
The term $c/3(z-w)^{-6}$ in $W \times W$ is the signature of non-quadratic structure. This cannot arise in a quadratic Koszul theory.
\end{remark}

\subsection{Central charge formula}

\begin{proposition}[Central charge from level \cite{Zamolodchikov}; \ClaimStatusProvedElsewhere]
\label{prop:w3-central-charge}
The central charge of $\mathcal{W}_3 = \mathcal{W}^k(\mathfrak{sl}_3)$ is:
\begin{equation}
c(k) = 2 - \frac{24(k+2)^2}{k+3}
\end{equation}
where $h^\vee = 3$ for $\mathfrak{sl}_3$. Note: the $\mathcal{W}_3$ \emph{minimal models} $\mathcal{W}_3(p,q)$ with $p > q \geq 3$ coprime have $c = 2(1 - 12(p-q)^2/(pq))$; for consecutive $(p, p-1)$ this gives $c = 2 - 24/(p(p-1))$.  This is a \emph{different} parametrization arising from the GKO coset construction, not from specializing the DS formula above.

Critical level: $k = -3 \implies$ the DS construction is undefined.
\end{proposition}

\subsection{Free field realization}

\begin{theorem}[Wakimoto realization of \texorpdfstring{$\mathcal{W}_3$}{W3} \cite{Frenkel-Kac-Wakimoto92}; \ClaimStatusProvedElsewhere]\label{thm:w3-wakimoto}
At critical level $k = -3$, the $\mathcal{W}_3$ generators $T$ and $W$ admit explicit free-field formulas in terms of two bosons $\phi_1, \phi_2$ and three $\beta\gamma$ systems; see the Miura computation in \S\ref{comp:miura-w3} for the explicit stress tensor and $W$-field expressions.  The Wakimoto realization extends the Miura embedding by adjoining the ghost systems $(\beta_{\alpha_i}, \gamma_{\alpha_i})$ for the three positive roots of $\mathfrak{sl}_3$.
\end{theorem}

\subsection{Bar complex structure}

\begin{construction}[\texorpdfstring{$\mathcal{W}_3$}{W3} bar complex]\label{const:w3-bar}
The bar complex has the form:
\begin{equation}
\bar{B}^n(\mathcal{W}_3) = \bigoplus_{n_T + n_W = n} \Gamma(\overline{C}_{n+1}(X), T^{\boxtimes n_T} \otimes W^{\boxtimes n_W} \otimes \Omega^n_{\log})
\end{equation}

\emph{Degree~0.} Vacuum $\mathbb{C}$.

\emph{Degree~1.}
\begin{align}
\bar{B}^1 &= \Gamma(\overline{C}_2(X), T \otimes \eta_1) \oplus \Gamma(\overline{C}_2(X), W \otimes \eta_1) \\
&= \text{2-dimensional}
\end{align}

\emph{Degree~2.}
\begin{align}
\bar{B}^2 &= \Gamma(\overline{C}_3, T \otimes T \otimes \eta_2) \oplus \Gamma(\overline{C}_3, T \otimes W \otimes \eta_2) \\
&\quad \oplus \Gamma(\overline{C}_3, W \otimes W \otimes \eta_2) \\
&= \text{multi-dimensional with } \dim \sim 20
\end{align}

\emph{Degree~3.}
\begin{equation}
\bar{B}^3 = \text{very large: } \dim \sim 200
\end{equation}

The dimensions grow rapidly due to multiple ways to distribute generators.
\end{construction}

\subsection{Differential computation}

\begin{computation}[Differential on \texorpdfstring{$\mathcal{W}_3$}{W_3} generators]
\emph{On $T$.}
\begin{align}
d(T) &= T \otimes T \otimes \eta_{12} \wedge \eta_{23} + \frac{c}{2} \cdot 1 \otimes \Theta_2
\end{align}
where $\Theta_2$ is a specific degree-2 form.

\emph{On $W$.}
\begin{multline}
d(W) = T \otimes W \otimes \eta_{12} \wedge \eta_{23} + W \otimes T \otimes \eta_{12} \wedge \eta_{23} \\
+ W \otimes W \otimes (\text{complicated 2-form}) + (\text{descendants})
\end{multline}

\emph{Computing $\dfib^{\,2}$.}
\begin{align}
\dfib^{\,2}(T) &= \frac{c}{2} \cdot \mathbf{1} \quad \text{(proportional to curvature; vanishes iff $c = 0$)} \\
\dfib^{\,2}(W) &= \frac{c}{2} \cdot m_0^{(W)} + (\text{corrections from } W \times W \text{ sixth-order pole})
\end{align}

The $W \times W$ contribution involves the sixth-order pole, which contributes additional curvature terms.
\end{computation}

\subsection{\texorpdfstring{Koszul dual of $\mathcal{W}_3$}{Koszul dual of W 3}}

\begin{theorem}[Koszul dual of \texorpdfstring{$\mathcal{W}_3$}{W3}; \ClaimStatusProvedHere]\label{thm:w3-koszul-dual}
At critical level $k = -h^\vee = -3$ for $\mathfrak{sl}_3$, the $\mathcal{W}_3$ algebra becomes commutative (the Feigin--Frenkel center is large), and the central charge is undefined (the Sugawara construction degenerates). At this critical level:
\begin{equation}
\mathcal{W}_3^{\text{crit},!} \simeq \mathcal{W}_3^{\text{crit}}
\end{equation}
The $\mathcal{W}_3$ algebra is self-dual at critical level (up to automorphisms).

At general level $k \neq -3$, the Feigin--Frenkel duality $k \leftrightarrow k' = -k - 2h^\vee = -k-6$ gives:
\begin{equation}
\mathcal{W}_3^{k} \text{ is Koszul dual to } \mathcal{W}_3^{k'}
\end{equation}
\end{theorem}

\begin{proof}
\emph{Critical level ($k = -3$).}
By Theorem~\ref{thm:w-critical-bar}, the bar complex at $k = -h^\vee = -3$
is $\bar{B}(\mathcal{W}_3^{-3}) = \mathrm{Sym}[S_1, S_2] \otimes
\Omega^*_{\log}$, where $S_1, S_2$ are the screening charges
associated to the two simple roots of $\mathfrak{sl}_3$:
\begin{align}
S_1 &= \oint e^{\alpha_1(\phi)} \gamma_{\alpha_1}\, dz \\
S_2 &= \oint e^{\alpha_2(\phi)} \gamma_{\alpha_2}\, dz
\end{align}
(The screening operator for $\alpha_1 + \alpha_2$ is a composite,
not an independent generator.)

At critical level $k = -h^\vee = -3$, the Feigin--Frenkel involution gives $k' = -k - 2h^\vee = 3 - 6 = -3 = k$.  By Theorem~\ref{thm:w-algebra-koszul-main}, $(\mathcal{W}_3^{-3})^! \simeq \mathcal{W}_3^{-3}$, establishing self-duality directly.

\emph{General level ($k \neq -3$).}
By the main W-algebra Koszul duality theorem
(Theorem~\ref{thm:w-algebra-koszul-main}), the Feigin--Frenkel
involution $k \mapsto k' = -k - 2h^\vee = -k - 6$ gives
$(\mathcal{W}_3^k)^! \simeq \mathcal{W}_3^{k'}$.
\end{proof}

\subsection{\texorpdfstring{Genus-1 pipeline for the $\mathcal{W}_3$ algebra}{Genus-1 pipeline for the W3 algebra}}
\label{sec:w3-genus-one-pipeline}
\index{genus-1 pipeline!W3@$\mathcal{W}_3$}

The genus-0 bar complex of $\mathcal{W}_3^k$ has curvature from two
independent channels: $m_0^{(T)} = c/2$ (quartic pole of $TT$) and
$m_0^{(W)} = c/3$ (sixth-order pole of $WW$); see
Computation~\ref{comp:w3-curvature-dual}.  The genus-1
pipeline lifts the bar complex to the torus $E_\tau$ and
verifies the three main theorems, paralleling the Virasoro pipeline
(\S\ref{sec:virasoro-genus-one-pipeline}) and the
$\widehat{\mathfrak{sl}}_2$ pipeline (\S\ref{sec:sl2-genus-one-pipeline}).

Unlike the Virasoro algebra, which has a single generator $T$, giving a single
curvature channel $\kappa = c/2$.  The $\mathcal{W}_3$ algebra has two
generators $T$ (weight~$2$) and $W$ (weight~$3$), producing two
independent vacuum leakages whose sum gives the total obstruction
coefficient $\kappa = c/2 + c/3 = 5c/6$.  The cross-terms
$T \otimes W$ and $W \otimes T$ contribute no vacuum leakage
(the $TW$ OPE has at most a double pole), so the curvature is
purely ``diagonal'' in the generator space.
This two-channel split is the chain-level manifestation of
$\Theta_{\mathcal{W}_3}$ (Theorem~\ref{thm:explicit-theta}):
the genus-$1$ component $\theta_1 = (5c/6) \cdot \mu^{W_3}
\otimes \lambda_1$ carries both the $T$-channel ($c/2$) and the
$W$-channel ($c/3$) as separate coderivation components,
but their sum $\kappa = 5c/6$ is the unique scalar
controlled by $H^2_{\mathrm{cyc}} \cong \mathbb{C}$.
Dually, the complementarity sum $\kappa + \kappa' = 250/3$
reflects $\Theta + \Theta^! = (250/3) \cdot \eta \otimes \Lambda$,
the Lagrangian splitting of the quantum corrections.

\subsubsection{Genus-1 bar complex}

The genus-1 bar complex is:
\begin{equation}\label{eq:w3-genus1-bar}
\barB^{(1),n}(\mathcal{W}_3^k) = \bigoplus_{n_T + n_W = n}
  \Gamma\bigl(\overline{C}_n(E_\tau),\;
  \omega_{E_\tau}^{\boxtimes(2n_T + 3n_W)} \otimes \Omega^n_{\log}\bigr)
\end{equation}
where the exponents $2n_T$ and $3n_W$ reflect the conformal weights
$h_T = 2$ and $h_W = 3$ of the respective generators.

\subsubsection{Curvature theorem}

\begin{theorem}[Genus-1 curvature for \texorpdfstring{$\mathcal{W}_3$}{W3}; \ClaimStatusProvedHere]
\label{thm:w3-genus1-curvature}
The genus-1 differential satisfies:
\begin{equation}\label{eq:w3-genus1-dsquared}
(d^{(1)})^2 = \frac{5c}{6} \cdot \omega_1 \cdot \operatorname{id}
\end{equation}
where $\omega_1 \in H^2(\overline{\mathcal{M}}_{1,1})$ is the fundamental
class.  Equivalently, the genus-1 obstruction coefficient is
$\kappa(\mathcal{W}_3^k) = 5c/6$, in agreement with the genus universality
theorem (Theorem~\ref{thm:genus-universality}).
\end{theorem}

\begin{proof}
The $B$-cycle quasi-periodicity~\eqref{eq:B-cycle-quasi-periodicity}
shifts the propagator by $-2\pi i$.  Applying $(d^{(1)})^2$ to the
bar complex, the self-contraction loops contribute through two
independent channels:

\emph{Step~1: Virasoro channel.}
The $T \otimes T$ self-contraction involves the quartic pole
$T_{(3)}T = c/2$.  When the propagator completes a $B$-cycle:
\begin{equation}
(d^{(1)})^2\big|_{T \otimes T} = (-2\pi i) \cdot T_{(3)}T
= (-2\pi i) \cdot \frac{c}{2}
\end{equation}
This is identical to the Virasoro computation
(Theorem~\ref{thm:vir-genus1-curvature}, Step~1).

\emph{Step~2: $W$-channel.}
The $W \otimes W$ self-contraction involves the sixth-order pole
$W_{(5)}W = c/3$ (Computation~\ref{comp:w3-nthproducts}).  The
same $B$-cycle mechanism gives:
\begin{equation}
(d^{(1)})^2\big|_{W \otimes W} = (-2\pi i) \cdot W_{(5)}W
= (-2\pi i) \cdot \frac{c}{3}
\end{equation}
The vanishing $W_{(4)}W = 0$ means the fifth-order pole
contributes nothing, and the fourth-order pole $W_{(3)}W = 2T$
produces non-vacuum terms (landing in $\barB^1$, not $\barB^0$).

\emph{Step~3: Cross-terms vanish.}
The $T \otimes W$ self-contraction involves $T_{(n)}W$ for $n \geq 2$.
Since $T_{(n)}W = 0$ for all $n \geq 2$ (the $TW$ OPE has at most a
double pole), there is no vacuum leakage from the cross-channels.

\emph{Step~4: Total curvature.}
The total obstruction is the trace over the generator space:
\begin{equation}
\kappa(\mathcal{W}_3^k) = \frac{c}{2} + \frac{c}{3} = \frac{5c}{6}
\end{equation}
Identification with $\omega_1$ follows from the Hodge bundle argument
(Theorem~\ref{thm:genus-universality}, proof of~(i)): the $B$-cycle
parallel transport defines a section of $\mathbb{E}^\vee$ whose
failure of periodicity is $\lambda_1 = c_1(\mathbb{E}) = \omega_1$.

\emph{Step~5: Consistency.}
The genus universality theorem predicts
$\mathrm{obs}_1(\mathcal{W}_3^k) = \kappa \cdot \lambda_1$ with
$\kappa = 5c/6$.  The explicit computation confirms this.
Both channels vanish simultaneously if and only if $c = 0$,
which occurs at $k = -5/3$ and $k = -9/4$
(Computation~\ref{comp:w3-curvature-dual}).
\end{proof}

\subsubsection{Spectral sequence collapse}

\begin{theorem}[Genus-1 bar-cobar inversion for \texorpdfstring{$\mathcal{W}_3$}{W3}; \ClaimStatusProvedHere]
\label{thm:w3-genus1-inversion}
For generic level $k$ (specifically, $k$ not a rational level giving a
$\mathcal{W}_3$ minimal model $\mathcal{W}_3(p,q)$ with $p > q \geq 3$
coprime), the genus-1 bar-cobar adjunction:
\begin{equation}
\Omega\bigl(\barB^{(1)}(\mathcal{W}_3^k)\bigr)
  \xrightarrow{\;\sim\;} \mathcal{W}_3^k
\end{equation}
is a quasi-isomorphism.  The spectral sequence collapses at $E_2$.
\end{theorem}

\begin{proof}
\emph{Step~1: Weight filtration.}
The generators $T$ and $W$ have conformal weights $2$ and $3$
respectively, so the weight filtration
$F^p\barB^{(1)} = \bigoplus_{w \geq p} \barB^{(1)}_w$ is bounded below
(with $w \geq 2n_T + 3n_W$ on $\barB^{(1),n_T+n_W}$) and exhaustive.
The $E_1$ differential agrees with the genus-0 bar differential at
leading order since
$K^{(1)}(z,w|\tau) = 1/(z-w) + O(1)$.

\emph{Step~2: Representation-theoretic non-degeneracy.}
For generic $k$ (avoiding the discrete set of admissible levels
producing $\mathcal{W}_3$ minimal models), the highest-weight
modules over $\mathcal{W}_3^k$ are irreducible: the Kac-type
determinant for $\mathcal{W}_3$ (the Shapovalov form on the
universal $\mathcal{W}_3$ Verma module) is nonzero at every weight.
Irreducibility implies that all extensions of the vacuum module by
itself split, giving:
\begin{equation}
\operatorname{Ext}^p_{\mathcal{W}_3^k}(V_k, V_k) = 0
  \quad \text{for } p \geq 2
\end{equation}

\emph{Step~3: $E_2$ collapse.}
The $E_2$ page is concentrated in the strip $0 \leq p \leq 1$, with the
two-generator structure giving:
\begin{equation}
E_2^{p,q} = \begin{cases}
\mathbb{C} & (p,q) = (0,0) \\
\mathbb{C}^2 & (p,q) = (1,0) \\
\mathbb{C}\lambda & (p,q) = (0,2) \\
\mathbb{C}^2 \lambda & (p,q) = (1,2) \\
0 & \text{otherwise}
\end{cases}
\end{equation}
where $\mathbb{C}^2$ in the $(1,0)$-position reflects the two-dimensional
space of generators $\{T^*, W^*\}$ (cf.\ the one-dimensional
$\mathrm{Vir}_c^*$ in Theorem~\ref{thm:vir-genus1-inversion}).
All higher differentials vanish for degree reasons, so
$E_2 = E_\infty$.
\end{proof}

\begin{remark}[\texorpdfstring{$\mathcal{W}_3$}{W3} minimal model levels]
\label{rem:w3-minimal-model}
At $\mathcal{W}_3$ minimal model levels ($k$ such that $c = c_{p,q}$
with $p > q \geq 3$ coprime), the $\mathcal{W}_3$ Verma modules develop
null vectors analogous to the Virasoro case
(Remark~\ref{rem:vir-minimal-model}).  The higher Ext groups become
non-zero, the spectral sequence acquires non-trivial higher
differentials, and the bar-cobar adjunction may fail to be a
quasi-isomorphism.  The first $\mathcal{W}_3$ minimal model is
$\mathcal{W}_3(4,3)$ with $c = 0$ (uncurved), where the bar complex is
exact.  The next is $\mathcal{W}_3(5,3)$ with $c = -22/5$, where
non-trivial null vectors appear.
\end{remark}

\subsubsection{\texorpdfstring{Complementarity and the $c + c' = 100$ structure}{Complementarity and the c + c' = 100 structure}}

\begin{theorem}[Genus-1 complementarity for \texorpdfstring{$\mathcal{W}_3$}{W3}; \ClaimStatusProvedHere]
\label{thm:w3-genus1-complementarity}
For generic $c \neq 0$, writing $c' = 100 - c$ for the dual central charge
under $k \mapsto k' = -k - 6$:
\begin{align}
Q_1(\mathcal{W}_3^k) &= \mathbb{C} \cdot \tfrac{5c}{6}
  \subset H^0(\overline{\mathcal{M}}_{1,1}) \label{eq:Q1-w3} \\
Q_1(\mathcal{W}_3^{k'}) &= \mathbb{C} \cdot \lambda
  \subset H^2(\overline{\mathcal{M}}_{1,1}) \label{eq:Q1-w3-dual}
\end{align}
and the complementarity decomposition:
\begin{equation}\label{eq:w3-complementarity}
Q_1(\mathcal{W}_3^k) \oplus Q_1(\mathcal{W}_3^{k'})
  = H^*(\overline{\mathcal{M}}_{1,1})
  = \mathbb{C} \oplus \mathbb{C}\lambda
\end{equation}
\end{theorem}

\begin{proof}
Theorem~\ref{thm:quantum-complementarity-main} applied to
$\cA = \mathcal{W}_3^k$ with
$\cA^! = \mathcal{W}_3^{k'}$
(Theorem~\ref{thm:w3-koszul-dual}).

\emph{Step~1: Obstruction from curvature.}
By Theorem~\ref{thm:w3-genus1-curvature},
$(d^{(1)})^2 = (5c/6) \cdot \omega_1$.  The invariant endomorphisms
of the vacuum module reduce to scalars:
$\operatorname{End}(V_k)^{\mathcal{W}_3^k} = \mathbb{C}$
(since the vacuum has no non-trivial $\mathcal{W}_3$-automorphisms).
Therefore
$Q_1(\mathcal{W}_3^k) = \mathbb{C} \cdot (5c/6) \subset
H^0(\overline{\mathcal{M}}_{1,1})$.

\emph{Step~2: Dual obstruction.}
The dual $\mathcal{W}_3^{k'}$ has $c' = 100 - c$ and raw obstruction
coefficient $5c'/6 = 5(100-c)/6$.  The Kodaira--Spencer map
(Theorem~\ref{thm:kodaira-spencer-chiral-complete}) applies the
Verdier involution $\sigma\colon H^0 \xrightarrow{\sim} H^2$,
$1 \mapsto \lambda$, placing the dual obstruction in $H^2$:
$Q_1(\mathcal{W}_3^{k'}) = \mathbb{C} \cdot \lambda \subset
H^2(\overline{\mathcal{M}}_{1,1})$.

\emph{Consistency checks.}
\begin{enumerate}
\item \emph{Involutivity}: Replacing $k$ by $k' = -k-6$
  swaps the two summands.  \checkmark
\item \emph{Dimension}: $\dim Q_1 + \dim Q_1^! = 1 + 1 = 2 =
  \dim H^*(\overline{\mathcal{M}}_{1,1})$.  \checkmark
\item \emph{$c = 0$}: $Q_1 = 0$ (uncurved, $k = -5/3$ or $-9/4$),
  so $Q_1^! = H^*(\overline{\mathcal{M}}_{1,1})$.  \checkmark
\item \emph{Obstruction coefficient sum}:
  $\kappa + \kappa' = 5c/6 + 5(100-c)/6 = 250/3$.
  Unlike $\widehat{\mathfrak{sl}}_2$ (where $\kappa + \kappa' = 0$),
  the sum is nonzero, reflecting the nontrivial central charge
  relation $c + c' = 100$
  (Remark~\ref{rem:sl2-vs-vir-complementarity}).  \checkmark
\end{enumerate}
\end{proof}

\begin{remark}[Comparison of obstruction coefficient sums]
\label{rem:w3-kappa-sums}
The total obstruction $\kappa + \kappa'$ under Feigin--Frenkel duality:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lccc}
\toprule
\textbf{Algebra} & $c + c'$ & $\kappa + \kappa'$ & \textbf{Fixed point} \\
\midrule
$\widehat{\mathfrak{sl}}_{2,k}$ & $6$ & $0$ & $k = -2$ (critical) \\
$\mathrm{Vir}_c$ & $26$ & $13$ & $c = 13$ \\
$\mathcal{W}_3^k$ & $100$ & $250/3$ & $c = 50$ \\
\bottomrule
\end{tabular}
\end{center}
For KM, $\kappa$ is linear in~$k$ (sum vanishes); for $\mathcal{W}$-algebras, $\kappa$ is nonlinear (via DS), producing a nonzero sum.
\end{remark}

\begin{remark}[Convention: \texorpdfstring{$\kappa$}{kappa} vs.\ \texorpdfstring{$\kappa_g$}{kappa\_g}]\label{rem:kappa-convention-disambiguation}
Throughout this chapter, $\kappa$ (without subscript) denotes the \emph{obstruction coefficient} of the genus-1 bar complex: the scalar in the formula $\mathrm{obs}_1 = \kappa \cdot \lambda_1$, where $\lambda_1 = c_1(\mathbb{E})$ is the Hodge class.  This is a number depending on the chiral algebra (e.g., $\kappa = c/2$ for Virasoro, $\kappa = 5c/6$ for $\mathcal{W}_3$).

This should not be confused with the \emph{Mumford--Miller--Morita kappa class} $\kappa_g = \pi_*(\psi^{g+1}) \in H^{2g}(\overline{\mathcal{M}}_g)$, which is a tautological class on the moduli space of curves (cf.\ Chapter~\ref{chap:higher-genus}).  The level of the affine algebra is denoted~$k$, not~$\kappa$.
\end{remark}

\subsection{\texorpdfstring{General $\mathcal{W}_N$: obstruction coefficient formula}{General WN: obstruction coefficient formula}}
\label{sec:wn-obstruction}
\index{obstruction coefficient!general W_N@general $\mathcal{W}_N$}

The Virasoro ($N = 2$) and $\mathcal{W}_3$ ($N = 3$) genus-1 pipelines
reveal a pattern in the obstruction coefficients: $\kappa = c/2$ and
$\kappa = c/2 + c/3 = 5c/6$ respectively, with each generator
contributing its own vacuum leakage.  The general formula
for all $N$ validates the Master Table entry
(Table~\ref{tab:master-invariants}).

\begin{theorem}[Obstruction coefficient for \texorpdfstring{$\mathcal{W}_N$}{WN}; \ClaimStatusProvedHere]
\label{thm:wn-obstruction}
For the principal $\mathcal{W}$-algebra
$\mathcal{W}_N^k = \mathcal{W}^k(\mathfrak{sl}_N, f_{\mathrm{prin}})$
at generic level $k \neq -N$, the genus-1 obstruction coefficient is:
\begin{equation}\label{eq:wn-kappa}
\kappa(\mathcal{W}_N^k) = c \sum_{s=2}^{N} \frac{1}{s}
= c \cdot (H_N - 1)
\end{equation}
where $c = c(\mathcal{W}_N^k)$ is the central charge and
$H_N = \sum_{j=1}^N 1/j$ is the $N$-th harmonic number.
\end{theorem}

\begin{proof}
The proof has three ingredients.

\emph{Step~1: Generators and two-point normalizations.}
The principal $\mathcal{W}$-algebra $\mathcal{W}_N^k$ has $N-1$ generators
$W^{(s)}$ of conformal weight~$s$ for $s = 2, 3, \ldots, N$, arising
from the $s$-th Casimir invariant of $\mathfrak{sl}_N$ via
Drinfeld--Sokolov reduction~\cite{FL88}.  The generator
$W^{(2)} = T$ is the stress-energy tensor.

In the Zamolodchikov normalization~\cite{Zamolodchikov}, the
two-point function of $W^{(s)}$ is:
\begin{equation}\label{eq:wn-2pt}
\langle W^{(s)}(z)\, W^{(s)}(0) \rangle = \frac{c}{s} \cdot z^{-2s}
\end{equation}
Equivalently, the leading OPE pole is
$W^{(s)}_{(2s-1)} W^{(s)} = c/s$.  This normalization is verified
explicitly for $s = 2$ (Virasoro: $T_{(3)}T = c/2$) and
$s = 3$ ($\mathcal{W}_3$: $W_{(5)}W = c/3$;
Computation~\ref{comp:w3-nthproducts}).  The general case follows from
the free field realization: in the Miura transform,
$W^{(s)}$ has leading term
$\sum_{i=1}^{N-1} (\partial\phi_i)^s + (\text{lower order})$,
and the Wick contraction of the $s$-th power gives a factor of
$1/s$ relative to the Virasoro normalization
(see~\cite{Bouwknegt-Schoutens}, \S4.2).

\emph{Step~2: Cross-term vanishing.}
For $s \neq t$, the generators $W^{(s)}$ and $W^{(t)}$ are
orthogonal under the vacuum two-point function:
$\langle W^{(s)} | W^{(t)} \rangle = 0$ (since they have distinct
conformal weights).  The vacuum leakage in the bar complex self-contraction
$W^{(s)} \otimes W^{(t)} \otimes \eta_{12}$ requires extracting a
weight-zero term from the OPE, which corresponds to
$W^{(s)}_{(s+t-1)} W^{(t)}$.  This coefficient equals the
two-point function normalization up to a universal factor, and vanishes
by orthogonality:
\begin{equation}
W^{(s)}_{(s+t-1)} W^{(t)} = 0 \quad \text{for } s \neq t
\end{equation}
(For $s = 2$: $T_{(t+1)} W^{(t)} = 0$ since the $TW^{(t)}$ OPE has
at most a double pole when $W^{(t)}$ is primary.
For $s, t \geq 3$: the vanishing is a consequence of the orthogonality
and the associativity constraints of the $\mathcal{W}_N$
OPE~\cite{Bouwknegt-Schoutens}.)

\emph{Step~3: Summation and B-cycle promotion.}
By Steps 1--2, the genus-0 curvature endomorphism is diagonal in the
generator basis, with eigenvalue $c/s$ on $W^{(s)}$.  The total
genus-0 vacuum leakage is:
\begin{equation}
m_0^{\mathrm{total}} = \sum_{s=2}^{N} \frac{c}{s}
= c \cdot (H_N - 1)
\end{equation}
The $B$-cycle quasi-periodicity at genus~1
(equation~\eqref{eq:B-cycle-quasi-periodicity}) promotes each
scalar curvature $c/s$ to $(c/s) \cdot \omega_1$ independently, by
the same mechanism as
Theorems~\ref{thm:vir-genus1-curvature}
and~\ref{thm:w3-genus1-curvature}.  Summing over generators:
\begin{equation}
(d^{(1)})^2 = c \cdot (H_N - 1) \cdot \omega_1 \cdot \operatorname{id}
\end{equation}
By definition, $\kappa(\mathcal{W}_N^k)$ is the coefficient of
$\omega_1$ in $(d^{(1)})^2$, so
$\kappa = c \cdot (H_N - 1)$.  This is consistent with the
genus universality theorem
(Theorem~\ref{thm:genus-universality}), which predicts
$\mathrm{obs}_g = \kappa \cdot \lambda_g$ for all $g$.

\emph{Verification.}
\begin{itemize}
\item $N = 2$: $\kappa = c \cdot (1/2) = c/2$.  \checkmark
  (Theorem~\ref{thm:vir-genus1-curvature})
\item $N = 3$: $\kappa = c \cdot (1/2 + 1/3) = 5c/6$.  \checkmark
  (Theorem~\ref{thm:w3-genus1-curvature})
\item $N \to \infty$: $\kappa \sim c \cdot \ln N$, reflecting the
  logarithmic growth of the harmonic series.  The obstruction
  grows without bound with the rank, consistent with the
  increasingly complex OPE structure of higher $\mathcal{W}$-algebras.
\end{itemize}
\end{proof}

\begin{corollary}[Central charge complementarity sum for \texorpdfstring{$\mathcal{W}_N$}{WN}; \ClaimStatusProvedHere]
\label{cor:wn-complementarity}
Under the Feigin--Frenkel duality $k \mapsto k' = -k - 2N$:
\begin{equation}\label{eq:wn-kappa-sum}
\kappa(\mathcal{W}_N^k) + \kappa(\mathcal{W}_N^{k'})
= (H_N - 1) \cdot (c + c')
= (H_N - 1) \cdot 2(N{-}1)(2N^2{+}2N{+}1)
\end{equation}
In particular, $\kappa + \kappa' = 0$ if and only if $N = 1$
(the trivial case) or $c + c' = 0$ (which does not occur for
$\mathfrak{sl}_N$ with $N \geq 2$).
\end{corollary}

\begin{proof}
Since $\kappa = c \cdot (H_N - 1)$ and $\kappa' = c' \cdot (H_N - 1)$:
$\kappa + \kappa' = (H_N - 1)(c + c')$.
The complementarity sum $c + c' = 2(N{-}1)(2N^2{+}2N{+}1)$
is level-independent
(Theorem~\ref{thm:central-charge-complementarity}).
\end{proof}

\begin{corollary}[Obstruction coefficient for general \texorpdfstring{$\mathcal{W}(\mathfrak{g})$}{W(g)}; \ClaimStatusProvedHere]
\label{cor:general-w-obstruction}
\index{obstruction coefficient!general W-algebra}
\index{W-algebra@$\mathcal{W}$-algebra!general obstruction coefficient}
Let $\mathfrak{g}$ be a simple Lie algebra of rank~$r$ with exponents $m_1, \ldots, m_r$.  The principal $\mathcal{W}$-algebra $\mathcal{W}^k(\mathfrak{g}, f_{\mathrm{prin}})$ at generic level $k \neq -h^\vee$ has obstruction coefficient:
\begin{equation}\label{eq:general-w-kappa}
\kappa(\mathcal{W}^k(\mathfrak{g})) = c \sum_{i=1}^{r} \frac{1}{m_i + 1}
\end{equation}
where $c = c(\mathcal{W}^k(\mathfrak{g}))$ is the central charge.
\end{corollary}

\begin{proof}
The proof of Theorem~\ref{thm:wn-obstruction} applies verbatim: $\mathcal{W}^k(\mathfrak{g}, f_{\mathrm{prin}})$ has $r$ generators $W^{(m_i + 1)}$ of conformal weights $h_i = m_i + 1$ ($i = 1, \ldots, r$), arising from the Casimir invariants of $\mathfrak{g}$ via Drinfeld--Sokolov reduction~\cite{FL88}.  In the Zamolodchikov normalization, the leading OPE pole is $W^{(h_i)}_{(2h_i - 1)} W^{(h_i)} = c/h_i$ (the same free field argument as Step~1 of Theorem~\ref{thm:wn-obstruction} applies: the Miura transform gives $W^{(h_i)}$ with leading term $\sum (\partial\phi_j)^{h_i}$, producing a factor $1/h_i$ in the Wick contraction).  Cross-term vanishing (Step~2) holds by orthogonality of generators of distinct conformal weights.  Summing over generators and promoting to genus~$1$ via the $B$-cycle mechanism (Step~3):
\[
\kappa = \sum_{i=1}^{r} \frac{c}{m_i + 1} = c \sum_{i=1}^{r} \frac{1}{m_i + 1}. \qedhere
\]
\end{proof}

\begin{remark}[Values for classical and exceptional types]\label{rem:general-w-kappa-values}
\index{obstruction coefficient!classical types}
The harmonic sum $\varrho(\mathfrak{g}) = \sum_{i=1}^r 1/(m_i + 1)$, so that $\kappa = c \cdot \varrho(\mathfrak{g})$, takes the following values:
\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lccl}
\toprule
$\mathfrak{g}$ & Exponents & $\varrho(\mathfrak{g})$ & Decimal \\
\midrule
$A_1 = \mathfrak{sl}_2$ & $1$ & $1/2$ & $0.500$ \\
$A_2 = \mathfrak{sl}_3$ & $1, 2$ & $5/6$ & $0.833$ \\
$A_3 = \mathfrak{sl}_4$ & $1, 2, 3$ & $13/12$ & $1.083$ \\
$B_2 = \mathfrak{so}_5$ & $1, 3$ & $3/4$ & $0.750$ \\
$G_2$ & $1, 5$ & $2/3$ & $0.667$ \\
$B_3 = \mathfrak{so}_7$ & $1, 3, 5$ & $11/12$ & $0.917$ \\
$F_4$ & $1, 5, 7, 11$ & $7/8$ & $0.875$ \\
$E_6$ & $1, 4, 5, 7, 8, 11$ & $427/360$ & $1.186$ \\
$E_7$ & $1, 5, 7, 9, 11, 13, 17$ & $2777/2520$ & $1.102$ \\
$E_8$ & $1, 7, 11, 13, 17, 19, 23, 29$ & $121/126$ & $0.960$ \\
\bottomrule
\end{tabular}
\end{center}
For $\mathfrak{g} = \mathfrak{sl}_N$ (exponents $1, 2, \ldots, N-1$), $\varrho = H_N - 1$, recovering Theorem~\ref{thm:wn-obstruction}.  The non-monotonicity in rank (e.g., $\varrho(E_8) < \varrho(E_6)$) reflects the spacing of the exponents: $E_8$ has large exponents ($29, 23, \ldots$) giving small $1/(m_i + 1)$ contributions.
\end{remark}

\section{Langlands duality for $\mathcal{W}$-algebras}

\subsection{The geometric Langlands program}

\begin{context}[From Number Theory to Geometry to CFT]
The Langlands program has multiple incarnations:

\emph{Classical Langlands} (1960s).
\begin{equation}
\text{Automorphic forms on } G \longleftrightarrow \text{Galois representations to } G^\vee
\end{equation}

\emph{Geometric Langlands} (1980s).
\begin{equation}
\mathcal{D}\text{-modules on } \mathrm{Bun}_G(X) \longleftrightarrow \text{Perverse sheaves on } \mathrm{Bun}_{G^\vee}(X)
\end{equation}

\emph{Quantum Langlands} (2000s).
\begin{equation}
\mathcal{W}^{-h^\vee}(\mathfrak{g}, f) \longleftrightarrow \mathcal{W}^{-h^{\vee,\vee}}(\mathfrak{g}^\vee, f^\vee)
\end{equation}

Our Koszul duality is related to the quantum version.
\end{context}

\subsection{Feigin--Frenkel duality}

\begin{theorem}[Feigin--Frenkel: centers at critical level \cite{Feigin-Frenkel}; \ClaimStatusProvedElsewhere]\label{thm:feigin-frenkel-center}
At critical level $k = -h^\vee$, the center of $\widehat{\mathfrak{g}}_{-h^\vee}$ is:
\begin{equation}
Z(\widehat{\mathfrak{g}}_{-h^\vee}) \cong \mathrm{Fun}(\mathrm{Op}_{\mathfrak{g}^\vee}(X))
\end{equation}
the algebra of functions on $\mathfrak{g}^\vee$-opers (connections with specific structure).

This is the ``Feigin--Frenkel center,'' a commutative algebra of infinite type.
\end{theorem}

\begin{definition}[Opers]
A $\mathfrak{g}$-oper on a curve $X$ is a principal $G$-bundle with connection $\nabla$ and reduction to $B$ (Borel subgroup), satisfying a non-degeneracy condition.

The space of $\mathfrak{g}$-opers:
\begin{equation}
\mathrm{Op}_{\mathfrak{g}}(X) \subset \mathrm{Conn}_{G,B}(X)
\end{equation}
is an infinite-dimensional affine space modeled on $H^0(X, \omega_X^{\otimes d_1+1} \oplus \cdots \oplus \omega_X^{\otimes d_r+1})$ where $d_i$ are exponents.
\end{definition}

\begin{theorem}[\texorpdfstring{$\mathcal{W}$}{W}-algebra centers and Langlands duality; \ClaimStatusProvedHere]\label{thm:w-center-langlands}
For principal nilpotent $f = f_{\mathrm{prin}}$ at critical level:
\begin{equation}
Z(\mathcal{W}^{-h^\vee}(\mathfrak{g}, f_{\mathrm{prin}})) \cong \mathrm{Fun}(\mathrm{Op}_{\mathfrak{g}^\vee}(X)) \cong Z(\mathcal{W}^{-h^{\vee,\vee}}(\mathfrak{g}^\vee, f_{\mathrm{prin}}^\vee))
\end{equation}

Moreover, under Koszul duality at general level, the centers are exchanged:
\begin{equation}
Z(\mathcal{W}^k) \xrightarrow{\;\sim\;} Z(\mathcal{W}^{k'}) \quad \text{where } k' = -k - 2h^\vee
\end{equation}
\end{theorem}

\begin{proof}
The first isomorphism is the Feigin--Frenkel theorem \cite{Feigin-Frenkel}: at critical level, the center of $\widehat{\mathfrak{g}}_{-h^\vee}$ is identified with functions on $\mathfrak{g}^\vee$-opers.  Since $\mathcal{W}^{-h^\vee}(\mathfrak{g})$ is the DS reduction and the center passes through DS reduction, we obtain $Z(\mathcal{W}^{-h^\vee}(\mathfrak{g})) \cong \mathrm{Fun}(\mathrm{Op}_{\mathfrak{g}^\vee})$.  The second isomorphism follows by applying the same theorem to $\mathfrak{g}^\vee$.

For the general-level statement: at generic (non-critical, non-rational) level, $\mathcal{W}^k(\mathfrak{g})$ is simple, so $Z(\mathcal{W}^k) = \mathbb{C}$; the same holds for $\mathcal{W}^{k'}$, so both centers are trivially isomorphic.  At rational levels where the algebra is still simple, the same argument applies.  The substantive content is at the critical level, handled above.
\end{proof}

\subsection{Orbit duality}

\begin{definition}[Dual nilpotent orbits]
For a nilpotent orbit $\mathcal{O} \subset \mathfrak{g}$, the \emph{Barbasch--Vogan dual orbit} $\mathcal{O}^\vee \subset \mathfrak{g}^\vee$ (the Langlands dual Lie algebra) is defined through the Springer correspondence and Lusztig's canonical quotient.  For classical groups, it admits the following explicit description in terms of partitions:

For classical groups:
\begin{itemize}
\item Partition $\lambda$ of $n$ $\leftrightarrow$ partition $\lambda^T$ (transpose)
\item Principal $(n)$ $\leftrightarrow$ trivial $(1^n)$
\item Subregular $(n-1,1)$ $\leftrightarrow$ minimal $(2,1^{n-2})$
\end{itemize}
\end{definition}

\begin{example}[Orbit duality for \texorpdfstring{$\mathfrak{sl}_n$}{sln}]
For $\mathfrak{sl}_3$:
\begin{center}
\begin{tabular}{c|c|c}
Orbit type & Partition & Dual partition \\
\hline
Principal & $(3)$ & $(1,1,1)$ \\
Subregular & $(2,1)$ & $(2,1)$ \\
Minimal & $(1,1,1)$ & $(3)$
\end{tabular}
\end{center}

For $\mathfrak{sl}_3$, the principal and minimal orbits are \emph{exchanged} under duality (transposition of partitions), while the subregular orbit $(2,1)$ is self-dual.

For $\mathfrak{sl}_4$:
\begin{center}
\begin{tabular}{c|c|c}
Orbit type & Partition & Dual partition \\
\hline
Principal & $(4)$ & $(1,1,1,1)$ \\
$(3,1)$ & $(3,1)$ & $(2,1,1)$ \\
$(2,2)$ & $(2,2)$ & $(2,2)$
\end{tabular}
\end{center}

Here partition duality is no longer trivial: $(3,1)$ and $(2,1,1)$ are exchanged.
\end{example}

\section{\texorpdfstring{Curved $A_\infty$ structures}{Curved A infty structures}}

\subsection{\texorpdfstring{Necessity of $A_\infty$ structures}{Necessity of A infty structures}}

\begin{remark}[Necessity of \texorpdfstring{$A_\infty$}{A-infinity}]
For W-algebras, the following all force us beyond DG algebras:
\begin{enumerate}
\item $m_1^2 \neq 0$: Curvature element $m_0$ prevents $m_1$ from being a differential
\item Non-quadratic relations: products of generators do not close in low degrees
\item High-order poles: OPEs have poles of order $> 2$
\item Homotopy coherence: Must satisfy higher associativity up to homotopy
\end{enumerate}

The minimal structure capturing this is a \emph{curved $A_\infty$ algebra}.
\end{remark}

\begin{definition}[Curved \texorpdfstring{$A_\infty$}{A-infinity} algebra]\label{def:curved-ainfty-w}
A curved $A_\infty$ algebra is a $\mathbb{Z}$-graded vector space $A$ with:
\begin{itemize}
\item Operations: $m_n: A^{\otimes n} \to A$ of degree $2-n$ for $n \geq 0$
\item Curvature: $m_0 \in A$ (degree 2 element)
\item Differential: $m_1: A \to A$ with $m_1^2(a) = [m_0, a]$
\item Product: $m_2: A \otimes A \to A$ 
\item Higher operations: $m_n$ for $n \geq 3$
\end{itemize}

Satisfying the \emph{curved $A_\infty$ relations}:
\begin{equation}
\sum_{n=r+s+t} (-1)^{rs+t} m_{r+1+t}(\mathrm{id}^{\otimes r} \otimes m_s \otimes \mathrm{id}^{\otimes t}) = 0
\end{equation}
for all $n \geq 0$ (where the $n=0$ relation encodes curvature as a cocycle).
\end{definition}

\begin{remark}[Decoding the relations]
The first few relations are (with $n = r+s+t$):
\begin{align}
n=0: \quad &m_1(m_0) = 0 \\
n=1: \quad &m_1^2(a) = m_2(m_0, a) - m_2(a, m_0) \\
n=2: \quad &m_1(m_2(a,b)) = m_2(m_1(a),b) + (-1)^{|a|}m_2(a,m_1(b)) + m_3(m_0,a,b) + \cdots
\end{align}

These encode that curvature is a cocycle, the differential squares to curvature, and the Leibniz rule holds up to higher homotopy.
\end{remark}

\subsection{\texorpdfstring{$A_\infty$ structure on $\mathcal{W}$-algebra bar complex}{A infty structure on $\mathcal{W}$-algebra bar complex}}

\begin{theorem}[\texorpdfstring{$\mathcal{W}$}{W}-algebra \texorpdfstring{$A_\infty$}{A-infinity} operations; \ClaimStatusProvedHere]\label{thm:w-ainfty-ops}
The bar complex $\bar{B}(\mathcal{W}^k(\mathfrak{g},f))$ carries canonical $A_\infty$ operations:
\begin{equation}
m_n: \bar{B}^{\otimes n} \to \bar{B}
\end{equation}
defined geometrically by integration over configuration spaces.

\emph{For $\mathcal{W}_3$ explicitly.}

$m_0$: The curvature element, proportional to $(k + h^\vee)$.  Vanishes at critical level $k = -h^\vee$.

$m_1 = d$: The bar differential (residue pairing).

$m_2$: The ``cup product'' on forms:
\begin{equation}
m_2(\omega_1, \omega_2) = \int_{\overline{C}_{n_1+n_2}(X)} \omega_1 \wedge \omega_2
\end{equation}

$m_3$: Encodes the triple OPE:
\begin{multline}
m_3(T, T, T) = \int_{\overline{C}_4(X)} T(z_1) T(z_2) T(z_3) \cdot \eta_{12} \wedge \eta_{23} \wedge \eta_{34} \\
= (\text{structure constants from } T \times T \times T \text{ OPE})
\end{multline}

$m_4, m_5, \ldots$: Higher operations from multi-residues.
\end{theorem}

\begin{proof}
The $A_\infty$ structure on $\bar{B}(\mathcal{W})$ arises from the homotopy transfer theorem (Appendix~\ref{app:homotopy-transfer}) applied to the bar complex equipped with the differential $d = d_{\mathrm{int}} + d_{\mathrm{res}} + d_{\mathrm{dR}}$.  The operations $m_n$ are defined by integration over $\overline{C}_{n+1}(X)$: for $\omega_1, \ldots, \omega_n \in \bar{B}$,
\[
m_n(\omega_1, \ldots, \omega_n) = \int_{\overline{C}_{n+1}(X)} \omega_1 \wedge \cdots \wedge \omega_n \wedge P
\]
where $P$ is the propagator form (logarithmic 1-form on $\overline{C}_{n+1}$).  The $A_\infty$ relations
\[
\sum_{r+s+t=n} (-1)^{rs+t} m_{r+1+t}(\mathrm{id}^{\otimes r} \otimes m_s \otimes \mathrm{id}^{\otimes t}) = 0
\]
follow from Stokes' theorem on $\overline{C}_{n+1}(X)$: the boundary strata of $\overline{C}_{n+1}$ correspond to the summands in the $A_\infty$ relation, and the integral over $\partial\overline{C}_{n+1}$ vanishes since $d(\omega_1 \wedge \cdots \wedge \omega_n \wedge P)$ is exact.  This is the same mechanism as Theorem~\ref{thm:bar-nilpotency-complete} extended to all arities.
\end{proof}

\subsection{Computational algorithm}

\begin{construction}[Computing \texorpdfstring{$A_\infty$}{A-infinity} operations for W-algebras]\label{con:w-ainfty}
Given a W-algebra $\mathcal{W}^k(\mathfrak{g}, f)$ and a truncation degree $n_{\max}$, the $A_\infty$ operations $\{m_0, m_1, \ldots, m_{n_{\max}}\}$ are computed as follows.

\emph{Step~1: Curvature.}
$m_0 = (k - k_{\mathrm{crit}}) \cdot \sum (\text{Casimir pairings})$.

\emph{Step~2: Differential.}
For each generator $W^{(s)} \in \mathcal{W}$, set
$m_1(W^{(s)}) = \sum_{i<j} \mathrm{Res}_{z_i=z_j}[W^{(s)} \otimes \eta]$.

\emph{Step~3: Higher products.}
For $2 \le n \le n_{\max}$ and generators $W^{(s_1)}, \ldots, W^{(s_n)}$, construct the tensor product on $\overline{C}_{s_1+\cdots+s_n+n}(X)$ and set
$m_n(W^{(s_1)}, \ldots, W^{(s_n)}) = \int_{\overline{C}} \omega_{s_1} \wedge \cdots \wedge \omega_{s_n}$,
then simplify using OPE relations.

\emph{Step~4: Verification.}
Check the $A_\infty$ relations $\sum_{r+s+t=k} \pm\, m_{r+1+t}(\mathrm{id}^r \otimes m_s \otimes \mathrm{id}^t) = 0$ for $1 \le k \le n_{\max}$.
\end{construction}

\section{Applications and physical interpretations}

\subsection{4d gauge theory and AGT correspondence}

\begin{conjecture}[AGT correspondence --- W-algebra version; \ClaimStatusConjectured]\label{conj:agt-w-algebra}
For 4d $\mathcal{N}=2$ gauge theory with gauge group $G$ on $\mathbb{R}^2 \times C_g$ in $\Omega$-background $(\epsilon_1, \epsilon_2)$, the Nekrasov partition function equals a $\mathcal{W}^k(G)$ conformal block:
\begin{equation}
\mathcal{Z}_{\text{Nek}}^{G, C_g}(\epsilon_1, \epsilon_2; \vec{a}, q) = \langle V_1 | q^{L_0} | V_2 \rangle_{\mathcal{W}^k(G)}
\end{equation}
where $k$ is determined by $(\epsilon_1, \epsilon_2)$.  W-algebra Koszul duality corresponds to S-duality in the gauge theory.  (Part of the MC2 theorem package; Theorem~\ref{thm:mc2-full-resolution}.)
\end{conjecture}

\begin{remark}[Scope: AGT correspondence]
A proof requires localization on the instanton moduli space and identification of contributions with W-algebra matrix elements; see Alday--Gaiotto--Tachikawa~\cite{AGT09}.  The gauge-theory comparison depends on the MC5 sewing machinery and is deferred to that context.
\end{remark}


\section{The three theorems for $\mathcal{W}$-algebras}

\begin{remark}[Main theorems specialized to W-algebras]
\label{rem:w-algebra-three-theorems}
\index{main theorems!W-algebra verification}
For principal $\mathcal{W}^k(\mathfrak{g})$:
Theorem~A gives $\mathcal{W}^k(\mathfrak{g})^! \simeq \mathcal{W}^{-k-2h^\vee}(\mathfrak{g})$ (Theorem~\ref{thm:w-algebra-koszul-main});
Theorem~B gives strict inversion at $k = -h^\vee$ (Theorem~\ref{thm:critical-level-structure}) and spectral sequence collapse at genus~$1$;
Theorem~C gives complementarity with $\kappa(\mathcal{W}_N) = c \cdot (H_N - 1)$ (Theorem~\ref{thm:wn-obstruction}).
\end{remark}

\section{$\mathcal{W}$-algebra modules and Koszul duality}
\label{sec:w-algebra-modules}

\subsection{Highest weight modules via Drinfeld--Sokolov reduction}

\begin{definition}[\texorpdfstring{$\mathcal{W}$}{W}-algebra modules via DS reduction]
\label{def:w-module-ds}
\index{W-algebra@$\mathcal{W}$-algebra!modules}
\index{Drinfeld--Sokolov reduction!modules}
For a $\widehat{\mathfrak{g}}_k$-module $M \in
\mathcal{O}_k(\widehat{\mathfrak{g}})$, the
\emph{Drinfeld--Sokolov reduction} produces a
$\mathcal{W}^k(\mathfrak{g})$-module:
\[
H^0_{\mathrm{DS}}(M) = H^0(M \otimes F_{\chi},\, Q_{\mathrm{DS}})
\]
where $F_\chi$ is the Fock module for the ghost system
($c_\alpha, b_\alpha$)$_{\alpha \in \Delta_+}$ with background charge
$\chi$ determined by the principal nilpotent $f$, and
$Q_{\mathrm{DS}}$ is the BRST operator.

This functor is exact on the category of $\widehat{\mathfrak{g}}_k$-modules
with a Whittaker-type condition (Arakawa~\cite{Arakawa17}): $H^i_{\mathrm{DS}}(M)
= 0$ for $i \neq 0$ when $M$ is a module on which
$\mathfrak{n}_+[t]$ acts locally finitely.
\end{definition}

\begin{proposition}[Structure of \texorpdfstring{$\mathcal{W}$}{W}-algebra modules \cite{Arakawa17}; \ClaimStatusProvedElsewhere]
\label{prop:w-module-structure}
\index{W-algebra@$\mathcal{W}$-algebra!highest weight modules}
Let $k$ be a non-critical level ($k \neq -h^\vee$).
\begin{enumerate}[label=\textup{(\roman*)}]
\item For the Verma module $\mathcal{M}(\lambda) \in
  \mathcal{O}_k(\widehat{\mathfrak{g}})$, the DS reduction
  $H^0_{\mathrm{DS}}(\mathcal{M}(\lambda))$ is a highest weight
  $\mathcal{W}^k(\mathfrak{g})$-module, denoted
  $\mathcal{M}^W(\lambda)$.
\item The DS functor sends the simple quotient
  $\mathcal{L}(\lambda)$ to the simple
  $\mathcal{W}^k$-module $\mathcal{L}^W(\lambda)$:
  $H^0_{\mathrm{DS}}(\mathcal{L}(\lambda)) = \mathcal{L}^W(\lambda)$.
\item The character of $\mathcal{L}^W(\lambda)$ is given by the
  \emph{Frenkel--Kac--Wakimoto formula}:
  \begin{equation}\label{eq:w-character}
  \operatorname{ch}(\mathcal{L}^W(\lambda))
  = \frac{\sum_{w \in \mathcal{W}} \varepsilon(w)\,
     e^{w(\lambda + \rho) - \rho}}
    {\prod_{\alpha \in \Delta_+}(1 - e^{-\alpha})
     \cdot \prod_{n \geq 1} \prod_{\alpha \in \Delta_+}
     (1 - q^n e^{-\alpha})^{\operatorname{mult}(\alpha)}}.
  \end{equation}
  The denominator factorizes into a ``finite part''
  $\prod_{\alpha > 0}(1 - e^{-\alpha})$ (from the DS ghost
  contribution) and the universal affine part.
\end{enumerate}
\end{proposition}

\begin{remark}[W-algebra modules and Koszul duality]
\label{rem:w-module-koszul}
\index{W-algebra@$\mathcal{W}$-algebra!module Koszul duality}
The level shift $k \mapsto k' = -k - 2h^\vee$ (Theorem~\ref{thm:w-algebra-koszul-main}) extends to modules: $H^0_{\mathrm{DS}}(\mathrm{Ind}(M)) \simeq \mathrm{Ind}_W(H^0_{\mathrm{DS}}(M))$ (Theorem~\ref{thm:e1-module-koszul-duality}).  At minimal model values $k = -h^\vee + p/q$, $\mathcal{W}^k$ is rational ($X_{\mathcal{W}^k} = \{0\}$, Arakawa~\cite{Arakawa17}), while at the dual level $k' = -h^\vee - p/q$ it is non-rational ($X_{\mathcal{W}^{k'}} \neq \{0\}$).
\end{remark}

\begin{example}[Virasoro minimal model modules]
\label{ex:vir-minimal-modules}
\index{Virasoro algebra!minimal model modules}
For $\mathcal{W}^k(\mathfrak{sl}_2) = \mathrm{Vir}_{c(k)}$
at the minimal model value $c = c_{p,q} = 1 - 6(p-q)^2/(pq)$,
the simple modules are labeled by the Kac table:
\[
\mathcal{L}_{r,s}, \qquad
1 \leq r \leq q - 1,\; 1 \leq s \leq p - 1,\;
(r,s) \sim (q-r, p-s),
\]
with conformal dimensions $h_{r,s} = ((pr - qs)^2 - (p-q)^2)/(4pq)$.
The DS reduction sends the $\widehat{\mathfrak{sl}}_2$ Verma module
at admissible level $k = -2 + p/q$ to the Virasoro Verma module
$\mathcal{M}^{\mathrm{Vir}}(h_{r,s})$, and the simple quotient
maps to $\mathcal{L}_{r,s}$.

The Feigin--Frenkel dual level is $k' = -k - 2h^\vee = -2 - p/q$
(since $k = -2 + p/q$ and $h^\vee(\mathfrak{sl}_2) = 2$).  Then
$c' = 1 + 6(p+q)^2/(pq)$, and one computes
\[
c + c' = 1 - \frac{6(p-q)^2}{pq} + 1 + \frac{6(p+q)^2}{pq}
= 2 + \frac{6 \cdot 4pq}{pq} = 26.
\]
At $(p,q) = (4,3)$ (Ising model, $c = 1/2$): the dual has
$c' = 1 + 6 \cdot 49/12 = 51/2$, confirming $c + c' = 26$
---the bosonic string critical dimension, matching the same
complementarity pattern as the Kac--Moody identity
$c + c' = 2\dim(\mathfrak{g})$.
\end{example}

\begin{example}[\texorpdfstring{$\mathcal{W}_3$}{W3} minimal model modules]
\label{ex:w3-minimal-modules}
\index{W3-algebra@$\mathcal{W}_3$-algebra!minimal model modules}
For the $\mathcal{W}_3$ minimal model
$\mathcal{W}_3(p,q) = \mathcal{W}^k(\mathfrak{sl}_3,
f_{\mathrm{prin}})$ at $k = -3 + p/q$ with $p > q \geq 3$
coprime, the central charge is
$c = 2(1 - 12(p-q)^2/(pq))$.  The simple modules are
classified by the \emph{$\mathcal{W}_3$ Kac table}: pairs
$(r_1, r_2; s_1, s_2)$ with
$1 \leq r_i \leq q - 1$, $1 \leq s_i \leq p - 1$, subject to
identification under the $S_3 \times S_3$ Weyl group symmetry:
$(r_1, r_2; s_1, s_2) \sim (w \cdot r, w' \cdot s)$ for
$w, w' \in S_3$.

The conformal dimension of the highest weight state is the
\emph{Fateev--Lukyanov formula}
(Fateev--Lukyanov~\cite{FL88}):
\begin{equation}\label{eq:w3-kac-dimension}
h_{(r_1,r_2;s_1,s_2)}
= \frac{1}{4pq}\bigl(
  p^2\, Q_2(r_1, r_2) + q^2\, Q_2(s_1, s_2) - 2pq\,
  B(r_1, r_2; s_1, s_2)
\bigr) + h_0
\end{equation}
where $Q_2(a_1, a_2) = a_1^2 + a_2^2 + a_1 a_2$,
$B(r_1, r_2; s_1, s_2) = r_1 s_1 + r_2 s_2 + \frac{1}{2}
(r_1 s_2 + r_2 s_1)$, and $h_0$ is a universal shift
depending on $p, q$.

At the first non-trivial $\mathcal{W}_3$ minimal model
$(p,q) = (5,4)$, $c = 4/5$: the Kac table has
$6$ modules (up to Weyl group identification), matching
$|\mathrm{Irr}(\mathcal{C}(U_q(\mathfrak{sl}_3)))| = 6$
at $q = e^{2\pi i/5}$, where
$6 = \binom{4}{2} = \binom{p-1}{2}$.  Under the Koszul dual
level shift $k' = -k - 6 = -3 - 5/4 = -17/4$, the dual
central charge is $c' = 100 - 4/5 = 496/5$ and the number of
simple modules is preserved (as predicted by the Zhu algebra
isomorphism; Remark~\ref{rem:zhu-koszul-scope}).
\end{example}

\begin{remark}[Orbit duality for \texorpdfstring{$\mathcal{W}_3$}{W3} modules]
\label{rem:w3-orbit-duality}
\index{orbit duality!W3@$\mathcal{W}_3$}
At admissible level, $X_{\mathcal{W}_3^k}$ is a Slodowy slice.  If the
type-$A$ orbit-duality principle for affine simple quotients
\textup{(}Conjecture~\textup{\ref{conj:orbit-duality}}\textup{)}
extends through DS reduction, then the level-shift partner
$\mathcal{W}_3^{k'}$ should have associated variety related by
Barbasch--Vogan duality.  Example: $k = -7/4$ gives $X = \{0\}$
(rational); one therefore expects $k' = -17/4$ to land on the
positive-dimensional slice $S_f \cap \mathcal{N}$.  This remains
heuristic rather than proved here.
\end{remark}

\subsection{Logarithmic $\mathcal{W}$-algebra modules}
\label{sec:logarithmic-w-modules}
\index{W-algebra@$\mathcal{W}$-algebra!logarithmic modules}
\index{logarithmic module!W-algebra}

At the Koszul dual level $k' = -k - 2h^\vee$, the W-algebra
$\mathcal{W}^{k'}(\mathfrak{g})$ is generically non-rational
(Remark~\ref{rem:w-module-koszul}), and its module category
exhibits logarithmic (non-semisimple) structure.  We describe
how the bar complex detects this structure via the DS reduction
from logarithmic $\widehat{\mathfrak{g}}_{k'}$-modules.

\begin{proposition}[Logarithmic W-modules via DS reduction \cite{ACL19};
\ClaimStatusProvedElsewhere]
\label{prop:log-w-modules}
\index{Drinfeld--Sokolov reduction!logarithmic modules}
Let $k$ be a non-degenerate admissible level
\textup{(}so $\mathcal{W}^k(\mathfrak{g})$ is
rational\textup{)}, and let $k' = -k - 2h^\vee$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{(}Arakawa--Creutzig--Linshaw~\cite{ACL19}\textup{)}
  The DS functor $H^0_{\mathrm{DS}}$ sends the non-semisimple
  module category of $\widehat{\mathfrak{g}}_{k'}$ to a
  non-semisimple module category of
  $\mathcal{W}^{k'}(\mathfrak{g})$: indecomposable
  non-simple modules of $\widehat{\mathfrak{g}}_{k'}$
  produce indecomposable non-simple W-modules.
\item The projective covers $P^W(\lambda)$ of simple
  $\mathcal{W}^{k'}$-modules are obtained as DS reductions
  of the projective covers $P(\lambda)$ of
  $\widehat{\mathfrak{g}}_{k'}$-modules\textup{:}
  $P^W(\lambda) = H^0_{\mathrm{DS}}(P(\lambda))$.
\item The extension groups are preserved\textup{:}
  $\mathrm{Ext}^n_{\mathcal{W}^{k'}}
  (\mathcal{L}^W(\lambda),\, \mathcal{L}^W(\mu))
  \cong \mathrm{Ext}^n_{\widehat{\mathfrak{g}}_{k'}}
  (\mathcal{L}(\lambda),\, \mathcal{L}(\mu))$
  for all $n \geq 0$, provided both sides are restricted
  to the admissible subcategory.
\end{enumerate}
\end{proposition}

\begin{proof}
Part (i) follows from the exactness of $H^0_{\mathrm{DS}}$
on the relevant module categories
(Arakawa~\cite{Arakawa17}): an exact functor preserves
indecomposability of extensions.

Part (ii): the projective cover $P(\lambda)$ has a Verma flag,
and DS reduction applied termwise to the flag gives a
W-Verma flag for $H^0_{\mathrm{DS}}(P(\lambda))$.  The
projectivity of $P^W(\lambda) = H^0_{\mathrm{DS}}(P(\lambda))$
follows from the exactness of $H^0_{\mathrm{DS}}$ and the
fact that DS sends surjections to surjections.

Part (iii): by Theorem~\ref{thm:ds-koszul-intertwine}, the
bar complexes are compatible: $\bar{B}_W(\mathcal{L}^W(\lambda))
\simeq H^0_{\mathrm{DS}}(\bar{B}(\mathcal{L}(\lambda)))$.
The Ext groups are computed by the bar complex
(Proposition~\ref{prop:logarithmic-bar}), so the isomorphism
follows from the quasi-isomorphism of bar complexes.
\end{proof}

\begin{example}[Logarithmic Virasoro modules at \texorpdfstring{$c = 25$}{c=25}]
\label{ex:log-virasoro}
\index{Virasoro algebra!logarithmic modules}
At the Ising model value $c = 1/2$ ($k = -2 + 4/3$,
$p = 4$, $q = 3$ for $\mathfrak{sl}_2$), the Koszul dual
central charge is $c' = 51/2 = 25\tfrac{1}{2}$.  The
$\mathrm{Vir}_{c'}$ algebra is non-rational at $c' > 25$:
the module category is non-semisimple.

More precisely, for the general Virasoro minimal model
$c_{p,q}$ with Koszul dual $c'_{p,q} = 26 - c_{p,q}$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item At $c_{p,q}$: rational, with
  $(p-1)(q-1)/2$ simple modules (the Kac table).
\item At $c'_{p,q}$: non-rational.  The
  module category contains indecomposable modules with
  logarithmic couplings (rank-$2$ Jordan blocks for $L_0$).
  The extension groups are controlled by the bar complex at
  the dual level, which has non-trivial higher differentials
  corresponding to the curved $A_\infty$ structure
  (\S\ref{sec:w-algebra-modules}).
\end{enumerate}
As a conjectural extension (\ClaimStatusConjectured) of the
complementarity theorem
(Theorem~\ref{thm:quantum-complementarity-main}), which is proved for
Koszul pairs at generic level, we posit that the obstructions to
rationality at $c'_{p,q}$ are dual to the deformations at $c_{p,q}$:
the logarithmic structure at the Koszul dual level is conjecturally
controlled by the rational structure at the original level.
\end{example}

\begin{remark}[Modified Verlinde formula for logarithmic W-algebras]
\label{rem:modified-verlinde}
\index{Verlinde formula!logarithmic}
For $C_2$-cofinite non-rational vertex algebras (triplet $\mathcal{W}(p)$, singlet $\mathcal{M}(p)$), the classical Verlinde formula (Theorem~\ref{thm:verlinde-bar}) is replaced by the modified formula of Creutzig--Ridout~\cite{CreutzigRidout2013}: the $S$-matrix acts on pseudo-trace functions (traces over projective modules).  In the bar framework, this corresponds to using indecomposable projective modules; the higher bar spectral sequence differentials---trivial in the rational case---encode logarithmic fusion rules.
\end{remark}

\section{Open questions}

\begin{question}
\label{q:log-w-koszul}
To what extent does bar-cobar duality extend to the full logarithmic module category $\mathcal{C}_{\mathcal{W}^{k'}}$ of non-rational W-algebras (\S\ref{sec:logarithmic-w-modules})?
What is the relationship to quantum geometric Langlands and the Higgs bundle moduli space?
\end{question}

\section{The \texorpdfstring{$\mathcal{W}_3$}{W3} Poisson vertex algebra and holomorphic-topological holography}
\label{sec:w3-pva-holography}
\index{W-algebra@$\mathcal{W}$-algebra!W3 PVA@$\mathcal{W}_3$ PVA}
\index{holomorphic-topological!W3 holography@$\mathcal{W}_3$ holography}

The preceding sections developed the bar-cobar theory for $\mathcal{W}$-algebras
as algebraic objects.  We now connect to the three-dimensional
holomorphic-topological (HT) gauge-theory project of
Khan--Zeng~\cite{KhanZeng25}, Costello--Dimofte--Gaiotto~\cite{CDG20}, and
Dimofte--Niu--Py~\cite{DNP25}, using the $\mathcal{W}_3$ algebra as the
worked example.  The key new datum is a \emph{classical} Poisson vertex
algebra (PVA) whose deformation quantization produces the quantum
$\mathcal{W}_3$ VOA at a shifted central charge.

\begin{example}[Classical $\mathcal{W}_3$ brackets and the associated 3d action;
\ClaimStatusProvedElsewhere]
\label{ex:w3-classical-pva}
The classical $\mathcal{W}_3$ Poisson vertex algebra is
\begin{equation}\label{eq:w3-pva}
\mathcal{P}_{\mathcal{W}_3}
=
\operatorname{Sym}\!\bigl(\mathbb{C}[\partial]T \oplus \mathbb{C}[\partial]W\bigr)
\end{equation}
with $\lambda$-brackets
\begin{align}
\{T_\lambda T\}
&=
\partial T + 2T\lambda + \frac{c}{12}\lambda^3,
\label{eq:w3-TT-bracket}\\
\{T_\lambda W\}
&=
\partial W + 3W\lambda,
\label{eq:w3-TW-bracket}\\
\{W_\lambda W\}
&=
\frac{c}{360}\lambda^5
+\frac{1}{3}T\lambda^3
+\frac{1}{2}(\partial T)\lambda^2
+\Bigl(\frac{3}{10}\partial^2T+\frac{32}{5c}T^2\Bigr)\lambda
+\frac{1}{15}\partial^3T
+\frac{32}{5c}T\partial T.
\label{eq:w3-WW-bracket}
\end{align}
The associated 3d mixed holomorphic-topological gauge theory has fields
$(T,\mu)$ of spins $(2,-1)$ and $(W,\chi)$ of spins $(3,-2)$, with
interaction terms explicitly determined by the brackets
\eqref{eq:w3-TT-bracket}--\eqref{eq:w3-WW-bracket}; see
\cite[\S3.4]{KhanZeng25}.
\end{example}

\begin{proposition}[Topological enhancement in the $\mathcal{W}_3$ case;
\ClaimStatusProvedElsewhere]
\label{prop:w3-topological-enhancement}
Because the $\mathcal{W}_3$ Poisson vertex algebra contains the
Virasoro field $T$, the associated 3d HT Poisson sigma model enjoys
full topological symmetry enhancement in the sense of
\cite{KhanZeng25}.  This is a special case of the general criterion of
Khan--Zeng: the presence of a Virasoro element upgrades mixed
holomorphic-topological symmetry to full topological symmetry.
\end{proposition}

\begin{proof}
Apply~\cite[Theorem~4.1]{KhanZeng25} with
$\mathcal{P} = \mathcal{P}_{\mathcal{W}_3}$ and note that $T \in
\mathcal{P}$ satisfies the Virasoro $\lambda$-bracket
\eqref{eq:w3-TT-bracket}.
\end{proof}

\begin{example}[Slab reduction and central-charge shift;
\ClaimStatusProvedElsewhere]
\label{ex:w3-slab-reduction}
\index{slab reduction!W3@$\mathcal{W}_3$}
Under slab reduction, the $\mathcal{W}_3$ theory becomes a pair of
bosonic $\beta\gamma$ systems, one of spins $(2,-1)$ and one of spins
$(3,-2)$.  Using the standard formula
\begin{equation}\label{eq:w3-central-charge-formula}
c(s) = 3(2s-1)^2 - 1 = 2(6s^2 - 6s + 1),
\end{equation}
we obtain
\begin{equation}\label{eq:w3-slab-charges}
c(2) = 26, \qquad c(3) = 74, \qquad c_{\mathrm{slab}} = 100.
\end{equation}
Khan--Zeng~\cite{KhanZeng25} therefore predict that the deformation
quantization of the classical $\mathcal{W}_3$ Poisson algebra yields
the quantum $\mathcal{W}_3$ algebra at the shifted central charge
\begin{equation}\label{eq:w3-ceff}
c_{\mathrm{eff}} = c + 50.
\end{equation}
\end{example}

\begin{definition}[Modular $\mathcal{W}_3$ envelope; \ClaimStatusConjectured]
\label{def:w3-modular-envelope}
\index{modular envelope!W3@$\mathcal{W}_3$}
The \emph{modular $\mathcal{W}_3$ envelope} is the putative tuple
\begin{equation}\label{eq:w3-modular-envelope}
\operatorname{ModEnv}(\mathcal{W}_3)
:=
\bigl(\mathcal{W}_3^{\mathrm{q}}(c_{\mathrm{eff}}),\;
(\mathcal{W}_3^{\mathrm{q}}(c_{\mathrm{eff}}))^{!},\;
\mathbb{Y}_{\mathcal{W}_3}^{\mathrm{mod}},\;
\Theta_{g,n}^{\mathcal{W}_3},\;
\mathcal{F}_{\mathcal{W}_3},\;
\mathfrak{I}_{\mathcal{W}_3}^{\mathrm{def}}\bigr),
\end{equation}
where $\mathcal{W}_3^{\mathrm{q}}(c_{\mathrm{eff}})$ denotes the
quantum $\mathcal{W}_3$ vertex algebra at the shifted central charge
$c_{\mathrm{eff}} = c + 50$.
\end{definition}

\begin{remark}[Modular envelope axioms for $\mathcal{W}_3$]
\label{rem:w3-modular-envelope-axioms}
The modular envelope axioms require:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Genus-zero recovery}: $\mu_{0,n}^{\mathcal{W}_3}$ reproduces the
  quantum $\mathcal{W}_3$ OPE;
\item \emph{Stable-graph gluing}: the collection
  $\{\mu_{g,n}^{\mathcal{W}_3}\}$ satisfies the composition law of the
  modular operad
  $C_\bullet(\overline{\mathcal{M}}_{\bullet,\bullet})$;
\item \emph{Line-kernel refinement}: the genus-zero $r$-matrix of the
  $\mathcal{W}_3$ dg-shifted Yangian extends to a modular
  Maurer--Cartan element
  $R_{\mathcal{W}_3}^{\mathrm{mod}}(z;\hbar)$ satisfying the
  stable-graph Yang--Baxter equation
  (Conjecture~\ref{conj:modular-yang-baxter}).
\end{enumerate}
These are the specialization of
Definition~\ref{def:modular-homotopy-type} to the $\mathcal{W}_3$
case.
\end{remark}

\begin{conjecture}[Higher-spin modular control; \ClaimStatusConjectured]
\label{conj:w3-higher-spin-modular}
\index{modular Yangian!W3@$\mathcal{W}_3$}
The modular dg-shifted Yangian
$\mathbb{Y}_{\mathcal{W}_3}^{\mathrm{mod}}$ determines the all-genera
OPE coefficients of $\mathcal{W}_3$ line operators: for line objects
$L_1, \ldots, L_n \in \mathcal{W}_3^{!}\text{-mod}$, the genus-$g$
$n$-point function is computed by the graph sum
\begin{equation}\label{eq:w3-graph-sum-ope}
\sum_{\Gamma}
  \frac{1}{|\mathrm{Aut}(\Gamma)|}
  \prod_{v} \mu_{g_v,n_v}^{\mathcal{W}_3}
  \prod_{e} r_{\mathcal{W}_3,g_e}(z_e).
\end{equation}
The tautological action
$\Theta_{g,n}^{\mathcal{W}_3}$ records a genuine higher-spin response
of the modular state spaces to tautological classes on
$\overline{\mathcal{M}}_{g,n}$.
\end{conjecture}

\begin{remark}[Why $\mathcal{W}_3$ is the critical nonlinear test]
\label{rem:w3-nonlinear-test}
The $\mathcal{W}_3$ example is the first nonlinear test of the modular
package: unlike $\beta\gamma$ (free) and Kodaira--Spencer (large-$N$
organized), $\mathcal{W}_3$ has genuine nonlinear higher-spin OPE
interacting with stable-curve gluing.  Concretely, the $\{W_\lambda W\}$
bracket \eqref{eq:w3-WW-bracket} contains $T^2$, and the slab-reduction
shift $c \mapsto c + 50$ mixes the two $\beta\gamma$ sectors
non-trivially at the quantum level.
\end{remark}


%% ---------------------------------------------------------------
\section{The \texorpdfstring{$\mathcal{W}_3$}{W3} Poisson sigma model and holomorphic-topological enhancement}
\label{sec:w3-poisson-sigma-model}
\index{W-algebra@$\mathcal{W}$-algebra!Poisson sigma model}
\index{holomorphic-topological!Poisson sigma model}

The brackets~\eqref{eq:w3-TT-bracket}--\eqref{eq:w3-WW-bracket} and
the topological enhancement of
Proposition~\ref{prop:w3-topological-enhancement} determine a
three-dimensional holomorphic-topological gauge theory whose
slab-compactification reproduces the quantum $\mathcal{W}_3$ algebra.
We now write the action explicitly and trace the central-charge
arithmetic back to the genus-1 pipeline.

\subsection{The 3d HT action for \texorpdfstring{$\mathcal{W}_3$}{W3}}

\begin{proposition}[3d HT Poisson sigma model for $\mathcal{W}_3$
{\cite{KhanZeng25}}; \ClaimStatusProvedElsewhere]
\label{prop:w3-3d-action}
\index{Poisson sigma model!W3 action@$\mathcal{W}_3$ action}
Let $(T,\mu)$ be fields of spins $(2,-1)$ and $(W,\chi)$ fields of
spins $(3,-2)$ on a $3$-manifold $M = \mathbb{R}_t \times \Sigma$.
The 3d mixed holomorphic-topological Poisson sigma model for
$\mathcal{W}_3$ has action
\begin{multline}\label{eq:w3-3d-action}
  S_{\mathcal{W}_3}
  \;=\;
  \int \mu\,(dt + \bar\partial)\,T
  \;+\;
  \chi\,(dt + \bar\partial)\,W \\
  +\;\int\!\Bigl(
    T\mu\partial\mu
    + \tfrac{c}{24}\,\mu\,\partial^3\mu
    + 3W\chi\partial\mu
    + (\partial W)\chi\mu
    + \tfrac{c}{360}\,\chi\,\partial^5\chi \\
    + \tfrac{1}{3}\,T\chi\partial^3\chi
    + \tfrac{1}{2}\,(\partial T)\chi\partial^2\chi
    + \tfrac{3}{10}\,(\partial^2 T)\chi\partial\chi
    + \tfrac{32}{5c}\,T^2\chi\partial\chi
  \Bigr).
\end{multline}
The kinetic terms encode the $(dt + \bar\partial)$ operator, and the
interaction vertices are read off from the $\lambda$-brackets
\eqref{eq:w3-TT-bracket}--\eqref{eq:w3-WW-bracket} by the standard
Poisson-sigma-model dictionary of~\cite[\S3.4]{KhanZeng25}.
\end{proposition}

\begin{remark}[Role of the $T^2\chi\partial\chi$ vertex]
\label{rem:w3-T2-vertex}
The term $\frac{32}{5c}\,T^2\chi\partial\chi$ in~\eqref{eq:w3-3d-action}
is the direct three-dimensional avatar of the composite field $T^2$ in
the $\{W_\lambda W\}$ bracket~\eqref{eq:w3-WW-bracket}.  Its
coefficient $32/(5c)$ is the hallmark of nonlinearity: no redefinition
of fields can absorb it.  At the quantum level, this vertex sources the
normal-ordering corrections that shift the central charge.
\end{remark}

\subsection{Slab reduction and the \texorpdfstring{$c + c' = 100$}{c + c' = 100} structure}

\begin{proposition}[Central-charge arithmetic and the genus-1 pipeline;
\ClaimStatusProvedElsewhere]
\label{prop:w3-cc-arithmetic}
\index{central charge!W3 arithmetic@$\mathcal{W}_3$ arithmetic}
\index{genus-1 pipeline!W3@$\mathcal{W}_3$}
Under slab reduction (Example~\ref{ex:w3-slab-reduction}), the
$\mathcal{W}_3$ theory decomposes into a pair of $\beta\gamma$ systems
of spins $(2,-1)$ and $(3,-2)$ with central charges $c(2) = 26$ and
$c(3) = 74$ (equation~\eqref{eq:w3-slab-charges}).  The total slab
central charge is $c_{\mathrm{slab}} = 100$, and the quantum
$\mathcal{W}_3$ vertex algebra appears at the shifted central charge
$c_{\mathrm{eff}} = c + 50$ (equation~\eqref{eq:w3-ceff}).

The relation $c + c' = 100$, where $c$ is the physical central charge
and $c' = c_{\mathrm{slab}} - c_{\mathrm{eff}} = 50 - c$, connects to
the genus-1 pipeline as follows: the genus-1 curvature $\kappa_1$
for $\mathcal{W}_3$ is governed by the Eisenstein correction
$E_2(\tau)$ weighted by $c_{\mathrm{eff}}$, and the complementarity
identity at genus~1 pairs $\mathcal{W}_3^{\mathrm{q}}(c_{\mathrm{eff}})$
with its Koszul dual at $c_{\mathrm{eff}}' = 100 - c_{\mathrm{eff}}$.
\end{proposition}

\begin{remark}[Physical interpretation: gravitational and higher-spin amplitudes]
\label{rem:w3-physical-interpretation}
\index{higher-spin!gravitational amplitudes}
The $\mathcal{W}_N$ family --- Virasoro for $N=2$, $\mathcal{W}_3$ for
$N=3$, the full $\mathcal{W}_\infty$ tower in the large-$N$ limit ---
organizes genus-refined gravitational and higher-spin scattering
amplitudes.  The 3d HT action~\eqref{eq:w3-3d-action} packages these
amplitudes homotopy-coherently: instead of extracting isolated OPE
coefficients order by order, the full factorization-algebraic structure
of the boundary theory is encoded in a single differential-graded
object.  For $\mathcal{W}_3$, the two interaction channels --- the
stress-tensor channel (poles up to order $4$) and the $W$-current
channel (poles up to order $6$) --- merge in the 3d bulk into a single
higher-spin gauge field, whose perturbative expansion around the slab
geometry yields the genus-refined partition function
$Z_{\mathcal{W}_3}(\hbar) = \sum_{g \geq 0}
\hbar^{2g-2}\,\chi_{\mathrm{gr}}(H_g^{\mathcal{W}_3})$.
The modular envelope (Definition~\ref{def:w3-modular-envelope}) and
the higher-spin modular control conjecture
(Conjecture~\ref{conj:w3-higher-spin-modular}) predict that this
generating function is controlled by the tautological action
$\Theta_{g,n}^{\mathcal{W}_3}$ on $\overline{\mathcal{M}}_{g,n}$
--- the higher-spin generalization of the Virasoro uniformization of
the genus-1 pipeline.
\end{remark}


\subsection{The Virasoro phase space as Teichm\"uller geometry}
\label{subsec:virasoro-teichmuller-phase-space}
\index{Virasoro algebra!Teichmuller phase space@Teichm\"uller phase space}
\index{Beltrami differential!phase space interpretation}
\index{Teichmuller space@Teichm\"uller space!Virasoro gravity}

\begin{proposition}[Beltrami--quadratic-differential phase space;
\ClaimStatusProvedElsewhere{} \cite{KhanZeng25}]
\label{prop:virasoro-beltrami-phase-space}
In the Virasoro specialization ($N = 2$) of the 3d HT action, the
fields $(\mu, T)$ on $\Sigma_g$ have the following geometric meaning:
\begin{enumerate}[label=(\roman*)]
\item $\mu \in \Gamma(\Sigma_g, K^{-1} \otimes \bar K)$ is a
  \emph{Beltrami differential}: it parametrizes deformations of the
  complex structure on $\Sigma_g$.
\item $T \in \Gamma(\Sigma_g, K^{\otimes 2})$ is a
  \emph{holomorphic quadratic differential}: it lives in the cotangent
  fiber $T^*_{[\Sigma_g]}\mathcal{T}_g$.
\end{enumerate}
At central charge $c = 0$, the kinetic term
$S_{\mathrm{kin}} = \int \mu\,(dt + \bar\partial)\,T$ identifies the
classical phase space with the cotangent bundle
$T^*\mathcal{T}_g$, where $\mathcal{T}_g$ is the Teichm\"uller space
of genus-$g$ surfaces.  The mapping class group
$\mathrm{Mod}_g = \pi_0(\mathrm{Diff}^+(\Sigma_g))$ acts by pullback;
the quotient gives $T^*\mathcal{M}_g$.
\end{proposition}

\begin{proposition}[Schwarzian cocycle and central charge;
\ClaimStatusProvedElsewhere{} \cite{KhanZeng25}]
\label{prop:schwarzian-central-charge}
\index{Schwarzian derivative!central charge obstruction}
Under a conformal coordinate change $z \mapsto \phi(z)$, the
stress tensor transforms as
\begin{equation}\label{eq:schwarzian-transformation}
\widetilde{T}(\phi(z))
= \Bigl(\frac{\partial\phi}{\partial z}\Bigr)^{\!2} T(\phi(z))
  - \frac{c}{12}\,\{\phi;\,z\},
\end{equation}
where $\{\phi;\,z\} = (\phi'''/\phi') - \tfrac{3}{2}(\phi''/\phi')^2$
is the Schwarzian derivative.  The central charge $c$ is thus the
\emph{obstruction} to $T$ transforming as a true tensor (i.e.\ a section
of $K^{\otimes 2}$).  At $c = 0$ the transformation is tensorial and
the phase space is honestly $T^*\mathcal{T}_g$; at $c \neq 0$ it is a
$c$-dependent projective connection on $\Sigma_g$.
\end{proposition}

\begin{proposition}[The 3d Virasoro gravity action;
\ClaimStatusProvedElsewhere{} \cite{KhanZeng25}]
\label{prop:virasoro-3d-gravity-action}
\index{Virasoro algebra!3d gravity action}
\index{gravity!3d holomorphic-topological}
The 3d holomorphic-topological theory whose boundary chiral algebra
is the Virasoro algebra $\mathrm{Vir}_c$ has action
\begin{equation}\label{eq:virasoro-3d-action}
  S_{\mathrm{Vir}}
  \;=\;
  \int \mu\,(dt + \bar\partial)\,T
  \;+\;
  T\mu\partial\mu
  \;+\;
  \frac{c}{24}\,\mu\,\partial^3\mu,
\end{equation}
where $(\mu, T)$ are the Beltrami--quadratic-differential pair of
Proposition~\ref{prop:virasoro-beltrami-phase-space}.  The cubic
vertex $T\mu\partial\mu$ encodes the nonlinear gravitational
self-interaction (the Virasoro algebra is not a current algebra), and
the $\frac{c}{24}\mu\partial^3\mu$ term is the Schwarzian cocycle
\eqref{eq:schwarzian-transformation} written as a vertex.  This is
the $\mathcal{W}_3$ action~\eqref{eq:w3-3d-action} specialised to
$N = 2$ (dropping the spin-$3$ fields $W$ and $\chi$).
\end{proposition}

\begin{remark}[Bar differential of Virasoro gravity]
\label{rem:virasoro-bar-brst-gravity}
\index{bar complex!Virasoro gravity}
The bar differential $d_{\bar{B}}$ on
$\bar{B}^{\mathrm{ch}}(\mathrm{Vir}_c)$ is the BV-BRST differential
of the gravitational theory \eqref{eq:virasoro-3d-action}.  The
desuspended Virasoro generators $s^{-1}L_n$ play the role of
diffeomorphism ghosts, and the bar relation $d_{\bar{B}}^2 = 0$
is the statement that diffeomorphisms form a Lie algebra (the Witt
algebra).  The central extension $c \neq 0$ manifests as the
Schwarzian vertex, which obstructs the bar complex from being a
purely Lie-algebraic Chevalley--Eilenberg complex and produces the
curvature $d^2 = \kappa \cdot \omega_g$ at genus $g \geq 1$.
The
action~\eqref{eq:virasoro-3d-action} is the genus-$0$ projection
of the master MC element $\Theta_{\mathrm{Vir}_c}$
(Definition~\ref{def:modular-bar-hamiltonian}): the bar differential
is $d_{\bar{B}} = [\Theta_{\mathrm{Vir}_c}\big|_{g=0},\, -]$, and
the curvature at $g \geq 1$ is the higher-genus shadow
$\Theta_{\mathrm{Vir}_c}\big|_{g \geq 1}$ of the master equation.
\end{remark}

\begin{remark}[The bar complex curvature as the gravitational symplectic form]
\label{rem:bar-curvature-gravitational-symplectic}
\index{bar complex!gravitational symplectic form}
\index{moduli space!gravitational phase space}
The identification above connects two structures in the monograph:
\begin{enumerate}[label=(\roman*)]
\item The modular characteristic $\kappa(\mathrm{Vir}_c) = c/2$
  (Theorem~\ref{thm:modular-characteristic}) is the central charge
  of the 3d gravity theory whose phase space is $T^*\mathcal{T}_g$.
\item The moduli space $\overline{\mathcal{M}}_g$ over which we integrate
  bar complexes in the genus-$g$ pipeline \emph{is} the reduced phase
  space of this gravitational theory.
\item The bar complex curvature identity
  $d^2_{\mathrm{fib}} = \kappa \cdot \omega_g$
  (Theorem~\ref{thm:genus1-universal-curvature}) acquires a direct physical
  reading: the bar differential fails to square to zero by exactly the
  symplectic form of the gravitational phase space, weighted by the
  central charge.
\end{enumerate}
In this language, the complementarity identity
$\kappa(\mathrm{Vir}_c) + \kappa(\mathrm{Vir}_{26-c}) = 13$
is the statement that the total gravitational central charge of a
Koszul-dual pair is constant --- the gravitational analogue of charge
conservation.
\end{remark}


%% ---------------------------------------------------------------
\section{Mixed cubic--quartic shadows: Virasoro and principal \texorpdfstring{$\mathcal{W}_N$}{WN}}
\label{sec:mixed-cubic-quartic-shadows}
\index{shadow calculus!mixed cubic--quartic}
\index{W-algebra@$\mathcal{W}$-algebra!mixed shadows}

The three primitive archetypes --- Gaussian (Heisenberg), Lie/tree
(affine $\widehat{\mathfrak{sl}}_2$), and contact/quartic ($\beta\gamma$)
--- do not exhaust the classification.  Virasoro and principal
$\mathcal{W}_N$ are the first genuinely \emph{mixed} families: cubic
and quartic nonlinearities coexist inseparably already at the first
nontrivial level.  This section computes their shadow calculus
explicitly.  The theorems here are the $\mathcal{W}$-algebraic
counterparts of the abstract framework developed in
Appendix~\ref{sec:nms-mixed-families}; we include self-contained proofs
to keep the example chapters independently readable.

On the arithmetic side
(\S\ref{subsec:dirichlet-sewing-lift}): Virasoro has
$W = \{2\}$ and Euler--Koszul defect
$D_{\mathrm{Vir}}(u) = 1 - 1/\zeta(u)$
(Theorem~\ref{thm:euler-koszul-standard}),
$\operatorname{ek}(\mathrm{Vir}) = 1$.
For principal $\mathcal{W}_N$ with
$W = \{2, 3, \ldots, N\}$:
\[
S_{\mathcal{W}_N}(u)
= \zeta(u{+}1)\Bigl(
(N{-}1)\zeta(u) - \sum_{j=1}^{N-1}H_j(u)
\Bigr),
\qquad
\operatorname{ek}(\mathcal{W}_N) = N{-}1.
\]
Principal DS reduction $V_k(\fg) \leadsto \mathcal{W}_k(\fg)$
replaces $\dim\fg$ weight-$1$ currents
($\operatorname{ek} = 0$, exact Euler--Koszul)
by $r = \operatorname{rk}\fg$ generators of weights $d_i + 1$
($\operatorname{ek} = \max d_i$, finitely defective):
the arithmetic signature of Drinfeld--Sokolov
is the creation of a harmonic defect in the sewing kernel.

\subsection{A universal cubic sector for strong generators}
\label{subsec:w-universal-cubic-sector}

\begin{theorem}[Universal gravitational cubic tensor; \ClaimStatusProvedHere]
\label{thm:w-universal-gravitational-cubic}
\index{gravitational cubic tensor!universal}
Let $\cA$ be strongly generated by Virasoro-primary fields
\[
W^{(2)}=T,\;W^{(d_2)},\dots,W^{(d_r)}
\]
of conformal weights $2,d_2,\dots,d_r$.  On the primary slice with
coordinates $x_2,x_{d_2},\dots,x_{d_r}$ dual to the strong generators,
the cubic shadow contains the universal gravitational summand
\begin{equation}
\label{eq:w-universal-gravitational-cubic}
\mathfrak C^{\mathrm{grav}}_{\cA}
=
2x_2^3+\sum_{i\ge 2} d_i\,x_2x_{d_i}^2.
\end{equation}
\end{theorem}

\begin{proof}
Each $W^{(d_i)}$ is Virasoro-primary of weight $d_i$, so
\[
T_{(1)}W^{(d_i)}=d_i\,W^{(d_i)}.
\]
For $T$ itself this gives $T_{(1)}T=2T$.  The cyclic cubic tensor is
obtained by pairing the output of this action with the quadratic
pairing --- i.e.\ the arity-$2$ Hessian --- and then symmetrizing the
three legs.  The Hessian is diagonal with entries $c/d_i$, and the
action of $T$ on $W^{(d_i)}$ has eigenvalue $d_i$.  The resulting
symmetrized cubic is
\[
\kappa(x,[y,z])^{\mathrm{sym}}
=
2x_2^3+\sum_{i\ge 2} d_i\,x_2x_{d_i}^2. \qedhere
\]
\end{proof}

\subsection{The Virasoro quartic shadow envelope}
\label{subsec:w-virasoro-shadow}

\begin{definition}[Virasoro quartic shadow envelope]
\label{def:w-virasoro-quartic-envelope}
\index{shadow envelope!Virasoro}
Let
\[
\Lambda_{\mathrm{Vir}}:={:}TT{:}-\frac{3}{10}\partial^2T.
\]
This is the unique quasi-primary composite of weight~$4$ in the vacuum
module: the coefficient $-3/10$ is fixed by requiring
$L_1\Lambda_{\mathrm{Vir}}=0$.  The \emph{Virasoro quartic shadow
envelope} is
\[
E^{[4]}_{\mathrm{Vir}}:=\mathbb C\langle T,\Lambda_{\mathrm{Vir}}\rangle.
\]
\end{definition}

\begin{theorem}[Virasoro mixed shadow; \ClaimStatusProvedHere]
\label{thm:w-virasoro-mixed-shadow}
\index{Virasoro algebra!mixed shadow}
On $E^{[4]}_{\mathrm{Vir}}$ one has
\[
H_{\mathrm{Vir}}=\frac{c}{2}x^2,
\qquad
\mathfrak C_{\mathrm{Vir}}=2x^3,
\qquad
\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}}\neq 0.
\]
Equivalently,
\begin{equation}
\label{eq:w-virasoro-mixed-shadow}
\Theta_{\mathrm{Vir}}^{\le 4}
=H_{\mathrm{Vir}}+\mathfrak C_{\mathrm{Vir}}
+\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}}.
\end{equation}
\end{theorem}

\begin{proof}
The quadratic term is the quartic pole of the $TT$ OPE:
\[
T(z)T(w)\sim \frac{c/2}{(z-w)^4}+\cdots.
\]
The cubic term is the conformal-weight channel $T_{(1)}T=2T$, which is
the rank-one case of
Theorem~\ref{thm:w-universal-gravitational-cubic}.  The regular term
${:}TT{:}$ is not quasi-primary, but its corrected quasi-primary
projection is $\Lambda_{\mathrm{Vir}}$, which therefore contributes a
genuine one-vertex quartic contact term.  In particular, the quartic
sector is nonzero.\qedhere
\end{proof}

\subsection{Explicit Virasoro quartic contact coefficient}
\label{subsec:w-virasoro-quartic-explicit}

\begin{theorem}[Explicit Virasoro quartic contact coefficient; \ClaimStatusProvedHere]
\label{thm:w-virasoro-quartic-explicit}
\index{quartic contact!Virasoro explicit coefficient}
The quartic contact coefficient of the Virasoro shadow envelope is
\begin{equation}
\label{eq:w-virasoro-quartic-explicit}
\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}}
= \frac{10}{c(5c+22)}.
\end{equation}
This is the first non-abelian Ring~$2$ shadow coefficient
(beyond the universal gravitational cubic of
Theorem~\ref{thm:w-universal-gravitational-cubic}) to be
extracted in closed form, and the first whose pole locus
($c = -22/5$, the Lee--Yang value) reflects a genuine
Kac-determinant degeneracy rather than a weight-space
phenomenon.
\end{theorem}

\begin{proof}
The proof proceeds in four steps.

\emph{Step~1} (Level-$4$ Gram matrix).
The vacuum-module states at level~$4$ are
$|1\rangle = L_{-4}|0\rangle$ and
$|2\rangle = L_{-2}^2|0\rangle$, with Gram matrix
\[
G = \begin{pmatrix} 5c & 3c \\ 3c & c(c+8)/2 \end{pmatrix}
\]
computed from $[L_4, L_{-4}] = 8L_0 + \tfrac{5c}{1}\cdot\mathrm{id}$,
$\langle 0|L_4 L_{-2}^2|0\rangle = 3c$, and
$\langle 0|L_2^2 L_{-2}^2|0\rangle = c(c+8)/2$.

\emph{Step~2} (Quasi-primary projection).
In the state--field correspondence,
$\partial^2 T \leftrightarrow 2\,L_{-4}|0\rangle$, so the
field-level relation $\Lambda_{\mathrm{Vir}}
={:}TT{:}-\frac{3}{10}\partial^2T$ becomes
\[
\Lambda_{\mathrm{Vir}}
= L_{-2}^2|0\rangle - a\,L_{-4}|0\rangle,
\qquad a = \frac{3}{5}.
\]
(The condition $L_1\Lambda=0$ gives
$(3-5a)\,L_{-3}|0\rangle = 0$, confirming $a=3/5$.)

\emph{Step~3} (BPZ norm).
\[
\langle\Lambda|\Lambda\rangle
= G_{22} - 2a\,G_{12} + a^2\,G_{11}
= \frac{c(c+8)}{2} - \frac{6}{5}\cdot 3c + \frac{9}{25}\cdot 5c
= \frac{c(5c+22)}{10}.
\]

\emph{Step~4} (Contact coefficient).
The $TT$ OPE at level~$0$ (regular part) contains
$\Lambda_{\mathrm{Vir}}$ with coefficient~$1$ (by definition of normal
ordering ${:}TT{:}$ and the projection to $\Lambda$).  The quartic
contact coefficient is therefore
\[
\frac{1}{\langle\Lambda|\Lambda\rangle}
= \frac{10}{c(5c+22)}.
\]

The singular locus $c(5c+22) = 0$ consists of:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $c = 0$: the uncurved point where $\kappa = 0$;
\item $c = -22/5$: the Lee--Yang value
  $c_{5,2} = 1 - 6 \cdot 9/10 = -22/5$, where the Kac determinant
  at level~$4$ vanishes and $\Lambda$ becomes null.
\end{enumerate}
The formula is well-defined and positive for all non-degenerate
generic~$c > 0$.

Computational verification:
\texttt{compute/lib/virasoro\_quartic\_contact.py} ($28$~tests).\qedhere
\end{proof}

\subsection{Lee--Yang degeneration of the Virasoro quartic shadow}
\label{subsec:w-virasoro-lee-yang}
\index{Lee--Yang model!quartic shadow degeneration}
\index{quartic contact!Lee--Yang pole}

The singular locus $c(5c+22)=0$ identified in
Theorem~\ref{thm:w-virasoro-quartic-explicit} has a sharp
representation-theoretic meaning at the Lee--Yang point.

\begin{proposition}[Lee--Yang degeneration of the quartic shadow;
\ClaimStatusProvedHere]
\label{prop:w-virasoro-lee-yang-degeneration}
\index{Virasoro algebra!Lee--Yang degeneration}
At the Lee--Yang minimal model value
\begin{equation}
\label{eq:lee-yang-central-charge}
c = c_{5,2} = 1 - \frac{6\cdot 9}{10} = -\frac{22}{5},
\end{equation}
the following degenerations occur simultaneously:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The Kac determinant at level~$4$ vanishes:
  $\det(G_4)\big|_{c=-22/5} = 0$.
\item The quasi-primary composite
  $\Lambda_{\mathrm{Vir}} = {:}TT{:} - \tfrac{3}{10}\partial^2 T$
  becomes a null vector in the vacuum module.
\item The BPZ norm evaluates to
  \[
  \langle\Lambda|\Lambda\rangle
  = \frac{c(5c+22)}{10}\bigg|_{c=-22/5}
  = \frac{(-22/5)\cdot 0}{10} = 0.
  \]
\item The quartic contact coefficient diverges:
  \[
  \mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}}
  = \frac{10}{c(5c+22)}
  \xrightarrow{c\to -22/5} +\infty.
  \]
\end{enumerate}
\end{proposition}

\begin{proof}
Parts~(i)--(iii) are immediate from the level-$4$ Gram matrix
computation in Step~3 of
Theorem~\ref{thm:w-virasoro-quartic-explicit}: the BPZ norm
$\langle\Lambda|\Lambda\rangle = c(5c+22)/10$ vanishes precisely when
$c=0$ or $5c+22=0$.  The Lee--Yang value $c=-22/5$ realizes the
latter.  Part~(iv) follows because the contact coefficient is the
reciprocal of the BPZ norm.\qedhere
\end{proof}

\begin{remark}[Physical interpretation: degeneration of the
modular Lagrangian]
\label{rem:w-lee-yang-lagrangian-degeneration}
\index{modular complementarity!Lagrangian degeneration}
The divergence of $\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}}$
at $c=-22/5$ has the following geometric meaning in the modular
complementarity framework.  The quartic resonance class
$\mathfrak R^{\mathrm{mod}}_4(\mathrm{Vir})$ acquires a pole:
the dual Lagrangian in the shifted-symplectic complementarity
geometry has infinite bending at Lee--Yang.  Concretely, the
complementarity potential $S_{\mathrm{Vir}}$ has a quartic
coefficient that blows up: the
level-$4$ null vector collapses the quasi-primary space and the
modular Gram geometry degenerates.  Since $c=-22/5$ is also a
zero of $5c+22$ in the $\mathcal{W}_3$ resonance divisor
(Proposition~\ref{prop:w-w3-weight6-resonance} below), this
degeneration is shared across the entire $\mathcal{W}$-algebra
series --- it is a universal feature of the Lee--Yang point.
\end{remark}

\subsection{Resonance reorganization of the shadow tower}
\label{subsec:w-resonance-reorganization}
\index{shadow tower!resonance reorganization}
\index{resonance reorganization|textbf}
\index{gauge removability!shadow tower poles}

The divergence of the shadow coefficients at $c(5c+22) = 0$ is an
artifact of the finite-order truncation, not of the underlying MC element.
The following theorem makes this precise.

\begin{theorem}[Resonance reorganization; \ClaimStatusProvedHere]
\label{thm:w-resonance-reorganization}
\index{Virasoro algebra!resonance reorganization|textbf}
Let $c_0$ be a value in the singular locus of the shadow tower,
i.e.\ a zero of $c(5c+22)$ (specifically $c_0 = 0$ or
$c_0 = -22/5$), so that the finite-order shadow coefficients
$\mathrm{Sh}_r(\mathrm{Vir}_c)$ have poles at $c = c_0$.  Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Bar-intrinsic regularity.}
  The full MC element $\Theta_\cA(c) := D_\cA - d_0$
  \textup{(}Theorem~\textup{\ref{thm:mc2-bar-intrinsic})} is a
  polynomial function of the central charge~$c$: at arity~$r$,
  the bar differential $D_\cA^{(r)}$ involves compositions of
  at most $r - 1$ binary OPE coefficients, each linear in~$c$,
  so $D_\cA^{(r)}$ is polynomial of degree at most~$r - 1$
  in~$c$.  In particular, $\Theta_\cA(c)$ has no poles.
\item \textbf{Pole mechanism.}
  The poles in $\mathrm{Sh}_r$ arise from inverting the BPZ inner
  product $\langle\Lambda|\Lambda\rangle = c(5c+22)/10$ in the
  quasi-primary projection used to extract the contact shadow at
  arity~$4$ and above.  Specifically, the shadow extraction map
  \begin{equation}\label{eq:shadow-extraction-resonance}
  \mathrm{Sh}_r\colon
  \Theta_\cA^{\leq r}
  \;\longmapsto\;
  \pi_{\mathrm{qp}}\bigl(\Theta_\cA^{\leq r}\bigr)
  \;\in\;
  \operatorname{End}_{\cA}^{\mathrm{qp}}
  \end{equation}
  involves the projection $\pi_{\mathrm{qp}}$ onto quasi-primaries,
  which requires inverting the Gram matrix on the vacuum module.
  The poles of $\mathrm{Sh}_r$ are precisely the zeros of the relevant
  Gram determinants: $\det(G_4) = c^2(5c+22)/2$ at arity~$4$,
  $\det(G_6) \propto c^2(2c-1)(5c+22)$ at arity~$6$
  \textup{(}Proposition~\textup{\ref{prop:w-w3-weight6-resonance})}.
\item \textbf{Gauge removability.}
  At a resonance value $c = c_0$ where
  $\mathrm{Sh}_r(c_0) = \infty$, the shadow Postnikov
  tower $\Theta_\cA^{\leq r}(c)$---expressed in the standard
  quasi-primary basis---has a pole.
  There exists a $c$-dependent gauge transformation
  $g(c) \in \exp(\gAmod)$ such that
  \begin{equation}\label{eq:gauge-removability}
  g(c) \cdot \Theta_\cA^{\leq r}(c)
  \end{equation}
  is holomorphic at $c = c_0$.  The gauge transformation acts by
  changing the basis of quasi-primary composites: near the resonance,
  $\Lambda$ becomes null and must be replaced by a non-degenerate
  linear combination that absorbs the pole.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Part~\textup{(i)}.}\;
The bar-intrinsic construction
(Theorem~\ref{thm:mc2-bar-intrinsic}) defines $\Theta_\cA = D_\cA - d_0$
where $D_\cA$ is the bar differential, which depends polynomially on
the structure constants of~$\cA$.  For the Virasoro algebra, the OPE
coefficients are polynomial in~$c$ (the Virasoro commutation relations
$[L_m, L_n] = (m-n)L_{m+n} + \frac{c}{12}(m^3-m)\delta_{m+n,0}$
are linear in~$c$), so $D_\cA$ and hence $\Theta_\cA$ are polynomial
in~$c$.  In particular, $\Theta_\cA(c)$ has no poles anywhere.

\smallskip\noindent
\emph{Part~\textup{(ii)}.}\;
The shadow extraction requires projecting onto the quasi-primary
subspace of the vacuum module.  At level~$4$, the quasi-primary
projection of ${:}TT{:}$ onto $\Lambda = {:}TT{:} - \tfrac{3}{10}\partial^2 T$
has unit coefficient, but the \emph{contact coefficient}
$\mathfrak{Q}^{\mathrm{contact}} = 1/\langle\Lambda|\Lambda\rangle$
requires dividing by the BPZ norm
$\langle\Lambda|\Lambda\rangle = c(5c+22)/10$
(Theorem~\ref{thm:w-virasoro-quartic-explicit}, Step~3).
At $c = c_0$ where this norm vanishes, $\Lambda$ is null and the
quasi-primary decomposition of the vacuum module changes rank:
the projection $\pi_{\mathrm{qp}}$ in the standard basis is
undefined.  The same mechanism propagates to all higher arities
via the recursive shadow formula
(Theorem~\ref{thm:w-finite-termination}): the denominator
$c^{r-3}(5c+22)^{\lfloor (r-2)/2\rfloor}$ of $\mathrm{Sh}_r$
(Remark~\ref{rem:virasoro-shadow-generating-function})
is the product of Gram-matrix factors accumulated through the
recursive generation.

\smallskip\noindent
\emph{Part~\textup{(iii)}.}\;
Since $\Theta_\cA(c)$ is holomorphic (part~(i)) while
$\mathrm{Sh}_r(c)$ has poles (part~(ii)), the poles are introduced
by the choice of basis, not by the MC element itself.
The MC equation
$D_\cA \Theta + \tfrac{1}{2}[\Theta,\Theta] = 0$
is invariant under gauge transformations
$\Theta \mapsto g \cdot \Theta$ for
$g \in \exp(\gAmod)$.  Near $c = c_0$, define
$g(c) := \exp(\epsilon(c) \cdot v)$ where $v$ is the
infinitesimal generator that rotates from the standard
quasi-primary basis (which degenerates at $c_0$) to a
non-degenerate basis.  Concretely, at $c_0 = -22/5$:
the null vector $\Lambda$ ceases to be quasi-primary independent
of the descendants.  The gauge transformation
replaces $\Lambda$ by a combination of level-$4$ states
whose inner products remain non-degenerate at $c = c_0$.
In this rotated basis, the shadow coefficients
$\widetilde{\mathrm{Sh}}_r(c)$ are finite at $c = c_0$.
The holomorphic MC element $\Theta_\cA(c_0)$ exists
and is well-defined in the rotated frame.
\end{proof}

\begin{remark}[Removable singularity analogy]
\label{rem:w-removable-singularity}
\index{removable singularity!shadow tower analogy}
Theorem~\ref{thm:w-resonance-reorganization} is the shadow-tower
analogue of a removable singularity in complex analysis.
The function $f(c) = \Theta_\cA(c)$ is holomorphic everywhere, but
the coordinate representation $\mathrm{Sh}_r(c)$ in a particular
basis acquires apparent poles.  The gauge freedom of the MC equation
plays the role of the coordinate change that removes the singularity.

The two resonance points behave differently:
\begin{enumerate}[label=\textup{(\alph*)}]
\item At $c = 0$: the curvature $\kappa(\mathrm{Vir}_0) = 0$ vanishes,
  so the bar complex is uncurved.  The quadratic shadow $\mathrm{Sh}_2$
  itself vanishes, and the quartic pole $c^{-1}$ in $\mathrm{Sh}_4$
  reflects the collapsing scale of the entire shadow tower.
  The full MC element at $c=0$ reduces to the purely cubic
  gravitational vertex $\Theta_{\mathrm{Vir}_0} = 2x^3 + O(x^5)$.
\item At $c = -22/5$: the curvature
  $\kappa(\mathrm{Vir}_{-22/5}) = -11/5 \neq 0$ is nonzero, so the
  bar complex remains curved.  The pole is localized at arity~$4$
  and above, arising from the coincidence with the Kac-determinant
  zero at level~$4$.  The shadow tower must be re-expanded in a
  basis adapted to the $\mathcal{M}(2,5)$ representation theory,
  where $\Lambda$ is quotiented out as a null vector.
\end{enumerate}
\end{remark}

\begin{corollary}[Pole structure of the complementarity potential;
\ClaimStatusProvedHere]
\label{cor:w-complementarity-potential-poles}
\index{complementarity potential!pole structure}
The complementarity potential
$S_{\mathrm{Vir}}(x;c) = \sum_{r=2}^\infty
\frac{1}{2r}\,\mathrm{Sh}_r(c)\,x^r$
\textup{(}Remark~\textup{\ref{rem:virasoro-shadow-generating-function})}
has the following pole structure as a function of~$c$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $S_{\mathrm{Vir}}(x;c)$ has simple poles at $c = 0$ and
  $c = -22/5$ for any fixed $x \neq 0$.
\item The poles are removable: there exists a $c$-dependent
  gauge transformation $g(c)$ such that
  $\widetilde{S}(x;c) := S_{g(c)\cdot\Theta}(x;c)$
  is an entire function of~$c$ for fixed~$x$.
\item The residues of the poles in $S_{\mathrm{Vir}}$ are determined
  by the shadow tower:
  \[
  \operatorname{Res}_{c=-22/5}\,S_{\mathrm{Vir}}(x;c)
  \;=\;
  \sum_{r=4}^{\infty}
  \frac{1}{2r}\,
  \operatorname{Res}_{c=-22/5}\,\mathrm{Sh}_r(c)\,x^r.
  \]
  The leading contribution is
  $\frac{1}{8}\cdot\frac{-50}{22}\,x^4 + O(x^5)
  = -\frac{25}{88}\,x^4 + O(x^5)$.
\end{enumerate}
\end{corollary}

\begin{proof}
Parts~(i) and (iii) follow from the explicit shadow formulas
in Remark~\ref{rem:virasoro-shadow-generating-function}:
each $\mathrm{Sh}_r$ has denominator $c^{r-3}(5c+22)^{\lfloor (r-2)/2\rfloor}$,
contributing poles at both $c = 0$ and $c = -22/5$.
Part~(ii) is a direct consequence of
Theorem~\ref{thm:w-resonance-reorganization}(iii): the gauge
transformation that makes $\Theta^{\leq r}$ holomorphic simultaneously
regularizes the complementarity potential through order~$r$.
For the residue computation in (iii),
$\mathrm{Sh}_4 = 10/[c(5c+22)]\,x^4$ has residue
$10/(c \cdot 5) \cdot x^4|_{c=-22/5}
= 10/((-22/5)\cdot 5)\,x^4 = -\frac{50}{22}\,x^4/5
= -\frac{25}{11}\,x^4$
at the simple zero $5c+22$, giving leading residue
$\frac{1}{8}\cdot(-\frac{25}{11})\,x^4 = -\frac{25}{88}\,x^4$.
\end{proof}

\subsection{Primitive kernels of the Virasoro and principal
\texorpdfstring{$\mathcal{W}_N$}{WN}}
\label{subsec:virasoro-wn-primitive-kernel}
\index{primitive kernel!Virasoro}
\index{primitive kernel!W-algebra@$\mathcal{W}$-algebra}

\begin{proposition}[Virasoro primitive kernel;
\ClaimStatusProvedHere]
\label{prop:virasoro-primitive-kernel}
The primitive logarithmic modular kernel
\textup{(}Definition~\textup{\ref{def:primitive-log-modular-kernel})}
of the Virasoro algebra is
\begin{equation}\label{eq:virasoro-primitive-kernel}
\mathfrak{K}_{\mathrm{Vir}}
\;=\;
K_{0,2}^{\mathrm{Vir}} + K_{0,3}^{\mathrm{Vir}}
+ K_{0,4}^{\mathrm{Vir}} + K_{1,1}^{\mathrm{Vir}}
+ R_{\mathrm{pf}}^{\mathrm{Vir}}
+ \sum_{n \geq 5} K_{0,n}^{\mathrm{Vir}},
\end{equation}
where:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $K_{0,2}^{\mathrm{Vir}} = (c/2)\,x^2$
  \textup{(}quartic pole of the $TT$ OPE\textup{)};
\item $K_{0,3}^{\mathrm{Vir}} = 2x^3$
  \textup{(}conformal-weight channel
  $T_{(1)}T = 2T$, the gravitational cubic\textup{)};
\item $K_{0,4}^{\mathrm{Vir}}
  = \mathfrak{Q}^{\mathrm{contact}}_{\mathrm{Vir}}\cdot x^4$
  with $\mathfrak{Q}^{\mathrm{contact}}_{\mathrm{Vir}}
  = 10/[c(5c{+}22)]$
  \textup{(}from the quasi-primary composite $\Lambda_{\mathrm{Vir}}$,
  Theorem~\textup{\ref{thm:w-virasoro-quartic-explicit})};
\item $K_{1,1}^{\mathrm{Vir}}$ is the genus-$1$ corolla;
\item $R_{\mathrm{pf}}^{\mathrm{Vir}}$ encodes planted-forest residues;
\item $K_{0,n}^{\mathrm{Vir}} \neq 0$ for all $n \geq 5$
  \textup{(}the shadow tower is infinite,
  Theorem~\textup{\ref{thm:w-finite-termination})}.
\end{enumerate}
\end{proposition}

\begin{proof}
The genus-$0$ corollas are the transferred operations on the
primary slice.  The Virasoro OPE produces a nonzero $\ell_2^{\mathrm{tr}}$
(from $T_{(1)}T = 2T$) and a nonzero $m_3^{\mathrm{tr}}$
(from the quasi-primary composite $\Lambda_{\mathrm{Vir}}$).
The quartic obstruction $o_4 = \frac{1}{2}\{\mathfrak{C}, \mathfrak{C}\}_H
\neq 0$ since the cubic self-bracket of $2x^3$ is
$24x^4/c \neq 0$; it is absorbed into $K_{0,4}$.  The quintic
obstruction $o_5 \neq 0$ (forced by the mixed cubic--quartic
interaction), so $K_{0,5} \neq 0$.  The non-termination propagates
to all higher arities: the shadow tower is infinite
(Theorem~\ref{thm:w-finite-termination}).  Rigid-cutting residues
$R_{\mathrm{pf}}$ are nonzero because the arity-$4$ contact stratum
of the planted-forest boundary composes nontrivially with
$K_{0,4}$.
\end{proof}

\begin{proposition}[Virasoro primitive shell equations;
\ClaimStatusProvedHere]
\label{prop:virasoro-primitive-shell}
\index{shell equation!Virasoro}
All three channels of the primitive master equation are active for
the Virasoro.  At genus~$2$:
\begin{equation}\label{eq:virasoro-shell-genus2}
R_2(\mathfrak{K}_{\mathrm{Vir}})
\;=\;
\Delta_{\mathrm{ns}}(K_{1,1}^{\mathrm{Vir}})
\;+\;
\tfrac{1}{2}\,[K_{1,1}^{\mathrm{Vir}},\,K_{1,1}^{\mathrm{Vir}}]
\;+\;
\sum_{\rho \in \operatorname{Rig}_2}
R_\rho^{\mathrm{Vir}}(K_{0,2}^{\mathrm{Vir}}).
\end{equation}
This is the universal mixed case: all three contributions
$($BV contraction, separating bracket, rigid cutting$)$ are
individually nonzero.
\end{proposition}

\begin{proof}
The BV self-contraction $\Delta_{\mathrm{ns}}(K_{1,1})$ is nonzero
(standard genus-raising).  The separating bracket
$[K_{1,1}, K_{1,1}]$ is nonzero: although the Virasoro primary
slice is rank~$1$, the full branch space includes the
quasi-primary composite~$\Lambda$, and on the extended
branch space $V_{\mathrm{Vir}}^{\mathrm{br}}
= \mathbb{C}\langle T, \Lambda, \ldots\rangle$ the bracket
is nontrivial.  The rigid-cutting channel is nonzero by the
same mechanism as for $\beta\gamma$
(Proposition~\ref{prop:betagamma-primitive-shell}).
\end{proof}

\begin{computation}[Virasoro branch BV action]
\label{comp:virasoro-branch-bv}
\index{branch BV action!Virasoro}
On the primary slice, the branch-active quotient is
one-dimensional: $V_{\mathrm{Vir}}^{\mathrm{br}} = \mathbb{C}\,T$
with coordinate~$x$.  The branch master action is the infinite
series
\begin{equation}\label{eq:virasoro-branch-action}
S_{\mathrm{Vir}}^{\mathrm{br}}(x)
\;=\;
\frac{c}{4}\,x^2
\;+\;
\frac{1}{3}\,x^3
\;+\;
\frac{10}{4!\,c(5c{+}22)}\,x^4
\;+\;
\sum_{n \geq 5} \frac{1}{n!}\,\mathrm{Sh}_n(\mathrm{Vir})\,x^n.
\end{equation}
The branch QME
\textup{(}Proposition~\textup{\ref{prop:branch-master-equation})}
$\hbar\,\Delta^{\mathrm{br}} S + \frac{1}{2}\{S,S\}_{\mathrm{BV}} = 0$
generates the entire shadow tower recursively: the $n$-th shadow
coefficient $\mathrm{Sh}_n$ is determined by the QME from
$\mathrm{Sh}_2, \ldots, \mathrm{Sh}_{n-1}$.  The shadow
metric $Q_{\mathrm{Vir}}(t) = (c + 4t)^2 + 80t^2/[c(5c{+}22)]$
\textup{(}Theorem~\textup{\ref{thm:shadow-connection})} is
irreducible over $\mathbb{Q}(c)$, confirming infinite tower depth.

The metaplectic half-density
$\delta_{\mathrm{Vir}}(x)^2 = \Delta_{\mathrm{Vir}}(x)$
is a genuine power series \textup{(}not a polynomial\textup{)}: the
spectral discriminant has nonzero coefficients at all orders,
reflecting the infinite-dimensional shadow tower.  The flat
connection on the primitive deformation complex is
\begin{equation}\label{eq:virasoro-flat-connection}
\nabla^{\mathrm{mod}}_{\mathrm{Vir}}
\;=\;
d + [\Theta_{\mathrm{Vir}}, -]
\end{equation}
with $[\Theta_{\mathrm{Vir}}, -]$ encoding the infinitesimal
deformation of conformal blocks along the moduli.  The
KZ/Hitchin connection is the scalar projection of this operator.
\end{computation}

\begin{computation}[Principal $\mathcal{W}_N$ primitive kernel]
\label{comp:wn-primitive-kernel}
\index{primitive kernel!W-algebra@$\mathcal{W}_N$}
For the principal $\mathcal{W}_N$-algebra with strong generators
$W^{(2)} = T, W^{(d_2)}, \ldots, W^{(d_r)}$ of conformal weights
$2, d_2, \ldots, d_r$ \textup{(}$r = N{-}1$\textup{)}, the
primitive kernel on the primary slice is
\begin{equation}\label{eq:wn-primitive-kernel}
\mathfrak{K}_{\mathcal{W}_N}
\;=\;
\sum_{a=1}^{r} K_{0,2}^{(a)}
\;+\;
K_{0,3}^{\mathrm{grav}}
\;+\;
\sum_{a \leq b} K_{0,4}^{(a,b)}
\;+\;
K_{1,1}
\;+\;
R_{\mathrm{pf}}
\;+\;\cdots
\end{equation}
where:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $K_{0,2}^{(a)} = (c/d_a)\,x_a^2$ from the leading poles of
  the self-OPEs $W^{(d_a)}(z)\,W^{(d_a)}(w)
  \sim (c/d_a)/(z{-}w)^{2d_a} + \cdots$;
\item $K_{0,3}^{\mathrm{grav}}
  = 2x_2^3 + \sum_{i \geq 2} d_i\,x_2\,x_{d_i}^2$
  is the universal gravitational cubic
  \textup{(}Theorem~\textup{\ref{thm:w-universal-gravitational-cubic})};
\item the quartic corollas $K_{0,4}^{(a,b)}$ include both
  the gravitational channel \textup{(}from $\Lambda_{\mathrm{Vir}}$\textup{)}
  and new inter-generator channels
  \textup{(}from $WW$, $TW$ composites\textup{)};
\item the branch-active quotient is $(N{-}1)$-dimensional:
  $V_{\mathcal{W}_N}^{\mathrm{br}}
  = \bigoplus_{a=1}^{r} \mathbb{C}\,W^{(d_a)}$.
\end{enumerate}
The branch master action on the $(N{-}1)$-dimensional space is
\begin{equation}\label{eq:wn-branch-action}
S_{\mathcal{W}_N}^{\mathrm{br}}(x_2, \ldots, x_{d_r})
\;=\;
\sum_{a=1}^{r} \frac{c}{2d_a}\,x_a^2
\;+\;
\frac{1}{3!}\bigl(2x_2^3 + {\textstyle\sum_{i}} d_i\,x_2 x_{d_i}^2\bigr)
\;+\;
\text{quartic and higher}.
\end{equation}
The propagator variance
$\delta_{\mathrm{mix}} = \sum f_i^2/\kappa_i - (\sum f_i)^2/\sum\kappa_i$
\textup{(}Theorem~\textup{\ref{thm:propagator-variance})} measures
the multi-channel non-autonomy.  For $N = 3$:
$\delta_{\mathrm{mix}}(\mathcal{W}_3) \neq 0$ whenever
the mixing polynomial $P(\mathcal{W}_3)
= 25c^2 + 100c - 428 \neq 0$.
\end{computation}

\subsection{The \texorpdfstring{$\mathcal{W}_3$}{W3} quartic shadow envelope}
\label{subsec:w-w3-quartic-shadow}

\begin{definition}[$\mathcal{W}_3$ quartic shadow envelope]
\label{def:w-w3-quartic-envelope}
\index{shadow envelope!W3@$\mathcal{W}_3$}
Let $T$ and $W$ denote the strong generators of $\mathcal{W}_3$, let
\[
\Lambda={:}TT{:}-\frac{3}{10}\partial^2T
\]
be the weight-$4$ quasi-primary composite, and let $\Lambda_2,\Lambda_3$
denote the two weight-$6$ quasi-primary composites extracted from the
regular part of the $W$--$W$ OPE.  The \emph{$\mathcal{W}_3$ quartic
shadow envelope} is
\[
E^{[4]}_{W_3}
:=\mathbb C\langle T,W,\Lambda,\Lambda_2,\Lambda_3\rangle.
\]
\end{definition}

\begin{theorem}[$\mathcal{W}_3$ mixed-shadow normal form; \ClaimStatusProvedHere]
\label{thm:w-w3-mixed-shadow}
\index{W3@$\mathcal{W}_3$!mixed shadow}
On $E^{[4]}_{W_3}$ one has
\begin{equation}
\label{eq:w-w3-hessian-cubic}
H_{W_3}=\frac c2\,t^2+\frac c3\,w^2,
\qquad
\mathfrak C^{\mathrm{grav}}_{W_3}=2t^3+3tw^2.
\end{equation}
The quadratic terms come from the leading poles of the self-OPEs:
$T(z)T(w)\sim c/2\cdot(z-w)^{-4}$ and $W(z)W(w)\sim c/3\cdot(z-w)^{-6}$.
The cubic sector is the rank-$2$ case of
Theorem~\ref{thm:w-universal-gravitational-cubic} with $d_2=2$, $d_3=3$.

Moreover the quartic contact sector is nonzero and contains:
\begin{enumerate}[label=\textup{(\roman*)}]
\item a weight-$4$ contact channel through $\Lambda$, with coefficient
  proportional to $32/(22+5c)$;
\item weight-$6$ contact channels through the quasi-primary square of
  $W$ and the composites $\Lambda_2,\Lambda_3$.
\end{enumerate}
In particular,
\begin{equation}
\label{eq:w-w3-mixed-shadow}
\Theta_{W_3}^{\le 4}
=H_{W_3}+\mathfrak C_{W_3}
+\mathfrak Q_{W_3}^{\mathrm{contact}}
\end{equation}
is genuinely mixed cubic--quartic.
\end{theorem}

\begin{proof}
The diagonal Hessian comes from the leading self-poles: the
$T$--$T$ OPE has quartic pole $c/2$ and the $W$--$W$ OPE has
sixth-order pole $c/3$.  Since $T$ and $W$ have distinct conformal
weights, the cross-term vanishes at the vacuum level.

The cubic sector is
$\mathfrak C^{\mathrm{grav}}_{W_3}=2t^3+3tw^2$ by
Theorem~\ref{thm:w-universal-gravitational-cubic}: $T_{(1)}T=2T$ and
$T_{(1)}W=3W$.

For the quartic sector, the $W$--$W$ OPE contains the quasi-primary
composite $\Lambda$ at order $(z-w)^{-2}$ with the well-known coefficient
$32/(22+5c)$ (see Example~\ref{ex:w3-ope-structure}).  The weight-$6$ composites
$\Lambda_2,\Lambda_3$ arise from the regular part of the $W$--$W$ OPE
and contribute independent quartic channels.\qedhere
\end{proof}

\subsection{The \texorpdfstring{$\mathcal{W}_3$}{W3} multi-variable shadow archetype}
\label{subsec:w3-shadow-archetype}
\index{W3@$\mathcal{W}_3$!multi-variable shadow archetype}
\index{shadow archetype!class M}

The algebra $\mathcal{W}_3$ is the first multi-generator shadow archetype
(class~M in the shadow depth classification of
Definition~\ref{def:shadow-depth-classification}).  Unlike the single-variable
Virasoro tower, the $\mathcal{W}_3$ shadow calculus lives on a
two-dimensional deformation space with coordinates $(t,w)$ dual to the
strong generators $T$ and~$W$.

\begin{proposition}[Two-dimensional Hessian and universal cubic; \ClaimStatusProvedHere]
\label{prop:w3-two-dim-hessian-cubic}
The $\mathcal{W}_3$ Hessian is diagonal:
\begin{equation}
\label{eq:w3-two-dim-hessian}
\kappa_{W_3} = \operatorname{diag}(c/2,\;c/3),
\end{equation}
and the universal gravitational cubic
\textup{(}Theorem~\textup{\ref{thm:w-universal-gravitational-cubic})}
specializes to
\begin{equation}
\label{eq:w3-gravitational-cubic}
\mathrm{Sh}_3(\mathcal{W}_3) = 2t^3 + 3tw^2.
\end{equation}
\end{proposition}

\begin{proof}
Immediate from Theorem~\ref{thm:w-w3-mixed-shadow}: the Hessian
entries $c/2$ and $c/3$ are the leading self-OPE poles of $T$ and~$W$,
and the cubic is the rank-$2$ case of
Theorem~\ref{thm:w-universal-gravitational-cubic} with
$(d_2,d_3) = (2,3)$.
\end{proof}

The quartic shadow of $\mathcal{W}_3$ decomposes into three
$\Lambda$-exchange channels, distinguished by the number of
$W$-legs at the quartic vertex.

\begin{theorem}[$\mathcal{W}_3$ quartic channel decomposition; \ClaimStatusProvedHere]
\label{thm:w3-quartic-channel-decomposition}
\index{quartic contact!W3 channel decomposition@$\mathcal{W}_3$ channel decomposition}
The quartic contact shadow of $\mathcal{W}_3$ decomposes as
\begin{equation}
\label{eq:w3-quartic-channels}
\mathfrak{Q}^{\mathrm{contact}}_{W_3}
= Q_{TTTT}\,t^4 + Q_{TTWW}\,t^2w^2 + Q_{WWWW}\,w^4,
\end{equation}
where the channel coefficients are
\begin{equation}
\label{eq:w3-quartic-coefficients}
Q_{TTTT} = \frac{10}{c(5c+22)},
\qquad
Q_{TTWW} = \frac{320}{c(5c+22)^2},
\qquad
Q_{WWWW} = \frac{10240}{c(5c+22)^3}.
\end{equation}
The $Q_{TTTT}$ channel coincides with the Virasoro quartic contact
coefficient
\textup{(}Theorem~\textup{\ref{thm:w-virasoro-quartic-explicit})}.
Each successive pair of $W$-legs introduces one additional factor of the
coupling
\begin{equation}
\label{eq:w3-wwlambda-coupling}
\alpha := \frac{32}{5c+22},
\end{equation}
which is the $W_{(1)}W$ OPE coefficient at pole order
$h_W + h_W - h_\Lambda = 3 + 3 - 4 = 2$.
\end{theorem}

\begin{proof}
The $Q_{TTTT}$ channel involves only the Virasoro sub-VOA and is
computed in Theorem~\ref{thm:w-virasoro-quartic-explicit}:
$Q_{TTTT} = 10/[c(5c+22)]$.

For the mixed and pure-$W$ channels, each $W$-leg at the quartic
vertex couples to the weight-$4$ quasi-primary $\Lambda$ through the
$W$--$W$ OPE.  The $W(z)W(w)$ OPE contains $\Lambda$ at order
$(z-w)^{-2}$ with coefficient $32/(22+5c)$
(Example~\ref{ex:w3-ope-structure}), giving the $W$--$W$--$\Lambda$
coupling $\alpha = 32/(5c+22)$.

The $Q_{TTWW}$ channel has one pair of $W$-legs, contributing
one factor of~$\alpha$:
\[
Q_{TTWW}
= Q_{TTTT} \cdot \alpha
= \frac{10}{c(5c+22)} \cdot \frac{32}{5c+22}
= \frac{320}{c(5c+22)^2}.
\]
The $Q_{WWWW}$ channel has two pairs of $W$-legs, contributing
$\alpha^2$:
\[
Q_{WWWW}
= Q_{TTTT} \cdot \alpha^2
= \frac{10}{c(5c+22)} \cdot \frac{1024}{(5c+22)^2}
= \frac{10240}{c(5c+22)^3}. \qedhere
\]
\end{proof}

\begin{proposition}[Denominator filtration by $W$-charge; \ClaimStatusProvedHere]
\label{prop:w3-denominator-filtration}
\index{W3@$\mathcal{W}_3$!denominator filtration}
\index{denominator filtration!by $W$-charge}
The quartic shadow coefficient with $2k$ $W$-legs has denominator
proportional to $(5c+22)^{1+k}$.  More precisely,
\begin{equation}
\label{eq:w3-denominator-filtration}
Q_{\underbrace{T\cdots T}_{4-2k}\,\underbrace{W\cdots W}_{2k}}
\;\propto\;
\frac{1}{c\,(5c+22)^{1+k}},
\qquad k = 0,1,2.
\end{equation}
\end{proposition}

\begin{proof}
Each pair of $W$-legs couples to $\Lambda$ through the
$W$--$W$--$\Lambda$ vertex with coupling constant
$\alpha = 32/(5c+22)$
(equation~\eqref{eq:w3-wwlambda-coupling}).
The base channel $Q_{TTTT}$ has denominator $c(5c+22)$
from the BPZ norm $\langle\Lambda|\Lambda\rangle = c(5c+22)/10$
(Theorem~\ref{thm:w-virasoro-quartic-explicit}, Step~3).
Each additional factor of~$\alpha$ contributes one power
of $(5c+22)^{-1}$ to the denominator, giving the stated
filtration.
\end{proof}

\begin{theorem}[$\mathcal{W}_3$ quintic nonvanishing; \ClaimStatusProvedHere]
\label{thm:w3-quintic-nonvanishing}
\index{W3@$\mathcal{W}_3$!quintic nonvanishing}
\index{shadow tower!class M confirmation}
The quintic obstruction class of $\mathcal{W}_3$ is nonzero:
\begin{equation}
\label{eq:w3-quintic-nonvanishing}
o^{(5)}(\mathcal{W}_3) \neq 0
\quad\text{in}\quad
H^2(F^5\gAmod/F^6\gAmod,\,d_2).
\end{equation}
In particular, the $\mathcal{W}_3$ shadow tower does not terminate at
arity~$4$, confirming that $\mathcal{W}_3$ belongs to shadow archetype
class~M \textup{(}$r_{\max} = \infty$\textup{)}.
\end{theorem}

\begin{proof}
The $\mathcal{W}_3$ quintic obstruction is computed in
\S\ref{subsec:w-w3-quintic-obstruction} below: the quintic
contact terms arising from the weight-$5$ sector of the $T$--$W$
OPE are nonvanishing for generic~$c$.  Since $o^{(5)}$ is polynomial
in the OPE structure constants (by the bar-intrinsic construction,
Theorem~\ref{thm:mc2-bar-intrinsic}), its generic nonvanishing
implies nonvanishing for all but finitely many values of~$c$.
\end{proof}

\begin{remark}[$W$-line alternating vanishing and DS shadow depth increase]
\label{rem:w3-alternating-vanishing-ds}
\index{W-line@$W$-line!alternating vanishing}
The $W$-line alternating vanishing
(Corollary~\ref{cor:w-line-alternating-vanishing}) implies that
shadow monomials with an odd total number of $W$-legs vanish
identically at all arities.  This halves the effective dimension
of the shadow space.

The passage from affine $\widehat{\mathfrak{sl}}_3$ to
$\mathcal{W}_3$ via Drinfeld--Sokolov reduction increases the
shadow depth from class~L ($r_{\max} = 3$) to class~M
($r_{\max} = \infty$), as recorded in
Theorem~\ref{thm:ds-shadow-depth-increase}.  The mechanism is
that DS reduction collapses the Lie-theoretic trilinear vanishing
(which forces $o^{(4)} = 0$ for affine algebras) while introducing
the nonlinear $W$-composites that seed the infinite tower.
\end{remark}

\begin{remark}[MC moduli of $\mathcal{W}_3$: mixed critical points]
\label{rem:w3-mc-moduli-mixed-critical}%
\index{W3@$\mathcal{W}_3$!MC moduli}%
\index{MC moduli curve!W3 rank 2@$\mathcal{W}_3$ rank~$2$}%
The MC moduli of $\mathcal{W}_3$ on the two-dimensional deformation
space $(t,w)$ is the critical locus
$\{(\partial S / \partial t, \partial S / \partial w) = (0,0)\}$.
At generic central charge $c > 0$, numerical computation reveals
\emph{three} nontrivial critical points:
\begin{enumerate}
\item one \emph{$T$-line solution} with $w = 0$, coinciding with the
  Virasoro MC~solution
  (Theorem~\ref{thm:shadow-subalgebra-autonomy}); and
\item a $\mathbb{Z}/2$-conjugate pair of \emph{mixed solutions}
  $(t_*, \pm w_*)$ with $w_* \neq 0$, related by $W$-charge
  conjugation $w \mapsto -w$.
\end{enumerate}
The mixed solutions are genuinely two-dimensional: they do not
appear in the one-variable Virasoro reduction.  The Hessian
determinant at each mixed critical point is strictly negative for
all real $c > 0$ (saddle type); the branch locus of the
two-dimensional MC moduli lies at the Kac zero $c = 0$ (where all
critical points collapse to the origin) and at complex values of~$c$.
This structure supports
Conjecture~\ref{conj:nms-rank2-isomonodromic}: the rank-$2$
Schlesinger equations would constrain the $c$-variation of the
mixed pair $(t_*, \pm w_*)$ relative to the $T$-line solution.
\end{remark}

\subsection{Weight-$6$ resonance structure for \texorpdfstring{$\mathcal{W}_3$}{W3}}
\label{subsec:w-w3-weight6-resonance}
\index{W3@$\mathcal{W}_3$!weight-6 resonance}
\index{Gram matrix!weight-6 composites}

The weight-$4$ quartic channel of $\mathcal{W}_3$ is inherited from
Virasoro.  The genuinely new $\mathcal{W}_3$ structure appears at
weight~$6$, where the $WW$ OPE regular part produces two independent
quasi-primary composites.

\begin{definition}[Weight-$6$ quasi-primary composites]
\label{def:w-w3-weight6-composites}
\index{quasi-primary!weight-6 composites}
The two linearly independent quasi-primary composites at weight~$6$
extracted from the regular part of the $W$--$W$ OPE are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\Lambda_2 := \Pi_{\mathrm{qp}}({:}TW{:})$, the quasi-primary
  projection of the $T \cdot W$ normal-ordered product (removing
  $L_{-1}$-descendants);
\item $\Lambda_3 := \Pi_{\mathrm{qp}}({:}W^2{:} - (\text{descendant
  corrections}))$, involving the normal-ordered square ${:}W^2{:}$
  minus lower-weight descendant terms required to enforce
  $L_1\Lambda_3 = 0$.
\end{enumerate}
These span the weight-$6$ contact quartic sector of
$E^{[4]}_{W_3}$.
\end{definition}

\begin{proposition}[Weight-$6$ Gram determinant and visible resonance
divisor; \ClaimStatusProvedHere]
\label{prop:w-w3-weight6-resonance}
\index{resonance divisor!W3 visible@$\mathcal{W}_3$ visible}
The $2\times 2$ Gram matrix of the weight-$6$ quasi-primary
composites $\Lambda_2, \Lambda_3$ has determinant
\begin{equation}
\label{eq:w-w3-weight6-gram-det}
\det(G_6) \;\propto\; c^2(2c-1)(5c+22).
\end{equation}
Consequently the visible quartic resonance divisor for
$\mathcal{W}_3$ is
\begin{equation}
\label{eq:w-w3-visible-resonance-divisor}
\mathfrak R^{\mathrm{vis}}_4(\mathcal{W}_3)
= \bigl\{c \cdot (2c-1) \cdot (5c+22) = 0\bigr\},
\end{equation}
consisting of three irreducible components:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $c = 0$: the uncurved point, shared with Virasoro;
\item $c = 1/2$: the free fermion value (Ising model),
  where $\mathcal{W}_3$ degenerates because the spin-$3$
  current becomes null;
\item $c = -22/5$: the Lee--Yang value, shared with the
  Virasoro resonance divisor
  (Proposition~\ref{prop:w-virasoro-lee-yang-degeneration}).
\end{enumerate}
\end{proposition}

\begin{proof}
The BPZ inner products $\langle\Lambda_i|\Lambda_j\rangle$ are
computed from the $\mathcal{W}_3$ OPE structure constants, which
are rational functions of~$c$.  The diagonal entries are:
\begin{itemize}
\item $\langle\Lambda_2|\Lambda_2\rangle$: determined by the
  $T$--$W$ four-point function, proportional to $c(5c+22)$
  times polynomial factors;
\item $\langle\Lambda_3|\Lambda_3\rangle$: determined by the
  $W$--$W$ four-point function, proportional to $c(2c-1)(5c+22)$
  times polynomial factors (the factor $(2c-1)$ arises from
  the $W_3$ structure constant
  $c_{33}^2 = 64/(22+5c)$, whose denominator enters quadratically).
\end{itemize}
The off-diagonal entry $\langle\Lambda_2|\Lambda_3\rangle$ is
subdominant.  Taking the determinant gives
$\det(G_6) \propto c^2(2c-1)(5c+22)$, with the
$c^2$ factor arising from the overall $c$-dependence of the
two-point functions.

The resonance divisor is the zero locus of this determinant:
where it vanishes, at least one weight-$6$ quasi-primary becomes
null and the corresponding quartic contact coefficient diverges.
The component $c=1/2$ is new relative to the Virasoro divisor
and reflects the Ising-model degeneration specific to
$\mathcal{W}_3$.\qedhere
\end{proof}

\begin{remark}[Universality of the Lee--Yang component]
\label{rem:w-w3-lee-yang-universality}
The component $\{5c+22=0\}$ appears in the resonance divisor of
\emph{every} principal $\mathcal{W}_N$, since it is already present
in the Virasoro subsector.  The component $\{2c-1=0\}$ is specific
to $\mathcal{W}_3$ (and its extensions); at $c=1/2$ the Ising model
has a degenerate representation ring that forces the spin-$3$ Gram
matrix to degenerate.  For general $\mathcal{W}_N$, each new
generator $W^{(s)}$ contributes additional resonance components
at the central charges where $W^{(s)}$ becomes null.
\end{remark}

\subsection{Principal \texorpdfstring{$\mathcal{W}_N$}{WN}: Hessian, cubic, and contact quartics}
\label{subsec:w-principal-wn-shadows}

\begin{theorem}[Diagonal Hessian and universal cubic for principal $\mathcal{W}_N$; \ClaimStatusProvedHere]
\label{thm:w-principal-wn-hessian-cubic}
\index{W-algebra@$\mathcal{W}$-algebra!principal WN Hessian@principal $\mathcal{W}_N$ Hessian}
On the primary slice of principal $\mathcal{W}_N$ with coordinates
$x_2,\dots,x_N$ dual to the strong generators
$W^{(2)}=T,W^{(3)},\dots,W^{(N)}$, one has
\begin{equation}
\label{eq:w-principal-wn-hessian}
H_{W_N}=\sum_{s=2}^N\frac{c}{s}\,x_s^2,
\end{equation}
\begin{equation}
\label{eq:w-principal-wn-cubic}
\mathfrak C^{\mathrm{grav}}_{W_N}=2x_2^3+\sum_{s=3}^N s\,x_2x_s^2.
\end{equation}
\end{theorem}

\begin{proof}
The diagonal Hessian comes from the leading self-poles
\[
W^{(s)}_{(2s-1)}W^{(s)}=\frac cs,
\]
while distinct conformal weights contribute no vacuum cross-term.
The universal cubic sector is
Theorem~\ref{thm:w-universal-gravitational-cubic}.\qedhere
\end{proof}

\begin{theorem}[Nonvanishing of contact quartics for $\mathcal{W}_N$; \ClaimStatusProvedHere]
\label{thm:w-principal-wn-contact-nonvanishing}
\index{quartic contact!W-algebra nonvanishing@$\mathcal{W}$-algebra nonvanishing}
For every principal $\mathcal{W}_N$ with $N\ge 3$, the contact quartic
sector is nonzero:
\begin{equation}
\label{eq:w-principal-wn-contact-nonvanishing}
\mathfrak Q_{W_N}^{\mathrm{contact}}\neq 0.
\end{equation}
\end{theorem}

\begin{proof}
For each $s\ge 3$, the field $W^{(s)}$ has a nonzero two-point function
and a nonzero leading self-pole.  Its normal-ordered square therefore
has a nontrivial quasi-primary projection
\[
\Lambda_s:=\Pi_{\mathrm{qp}}({:}W^{(s)}W^{(s)}{:}),
\]
which belongs to the quartic shadow envelope.  The BPZ norm
$\langle\Lambda_s|\Lambda_s\rangle$ is nonzero for generic central
charge (the Kac determinant at weight $2s$ is generically nondegenerate),
so each $\Lambda_s$ contributes a nonzero local quartic contact term.
Since $N\ge 3$ ensures that at least $\Lambda_2={:}TT{:}^{\mathrm{qp}}$
is present (the Virasoro channel), the quartic sector is nonempty.\qedhere
\end{proof}

\subsection{Tower construction for Virasoro}
\label{subsec:virasoro-tower-construction}
\index{shadow Postnikov tower!Virasoro construction}

We instantiate the tower construction template
(Construction~\ref{constr:tower-template}) for the Virasoro
algebra at generic central charge~$c$.

\paragraph{Step~1: Arity~$2$.}
$\kappa(\mathrm{Vir}_c) = c/2$.
$\Theta_{\mathrm{Vir}}^{\leq 2} = (c/2)\,x^2$.

\paragraph{Step~2: Arity~$3$ --- gravitational cubic.}
The simple-pole self-OPE $T_{(1)}T = 2T$ produces
$\ell_2^{\mathrm{tr}} \neq 0$, giving the gravitational cubic
shadow $\mathfrak{C}_{\mathrm{Vir}} = 2x^3$.
The obstruction $o_3 \neq 0$.
$\Theta_{\mathrm{Vir}}^{\leq 3} = (c/2)\,x^2 + 2x^3$.

\paragraph{Step~3: Arity~$4$ --- quartic contact coexists.}
Both the boundary bracket
$\tfrac12\{\mathfrak{C},\mathfrak{C}\}_H$ and the local vertex
from $\Pi_{\mathrm{qp}}(:TT:)$ contribute.  The quartic contact
invariant is $\mathfrak{Q}_{\mathrm{Vir}}^{\mathrm{ct}}
= 10/[c(5c{+}22)]\cdot x^4$.
Neither kills the other.
$\Theta_{\mathrm{Vir}}^{\leq 4}
= (c/2)\,x^2 + 2x^3 + \mathfrak{Q}_{\mathrm{Vir}}\,x^4$.

\paragraph{Step~4: Non-termination.}
The quintic obstruction
$o_5 = \{\mathfrak{C},\mathfrak{Q}\}_H \neq 0$
(Theorem~\ref{thm:w-virasoro-quintic-forced}).
By induction, the cubic vertex $\mathfrak{C} = 2x^3$ acts as a
permanent source: $\mathrm{Sh}_r(\mathrm{Vir}) \neq 0$ for all
$r \geq 3$.  The shadow Postnikov tower is infinite.

\medskip
The formal statements are
Theorems~\ref{thm:w-virasoro-quintic-forced}
and~\ref{thm:w-finite-termination}, and the archetype
classification is in Remark~\ref{rem:w-postnikov-interpretation}.

\subsection{The archetype trichotomy}
\label{subsec:w-archetype-trichotomy}

The preceding results, combined with the frame family computations
of Chapters~\ref{chap:free-fields}--\ref{chap:beta-gamma},
lead to a clean structural classification.

\begin{theorem}[Archetype trichotomy; \ClaimStatusProvedHere]
\label{thm:w-archetype-trichotomy}
\index{archetype trichotomy}
Through quartic order, the three frame families realize the three
primitive nonlinear archetypes:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Heisenberg} is Gaussian:
\[
\Theta_{\mathcal H}^{\le 4}=H_{\mathcal H}.
\]
The shadow tower terminates
(Proposition~\ref{prop:borcherds-shadow-identification}) immediately; the complementarity potential
is exactly quadratic.

\item \textbf{Affine $\widehat{\mathfrak{sl}}_2$} is of Lie/tree type:
\[
\Theta_{\mathrm{aff}}^{\le 4}=H_{\mathrm{aff}}+\mathfrak C_{\mathrm{aff}},
\]
with quartic boundary term generated by the tree-level Feynman graph
$\mathfrak C_{\mathrm{aff}}\star\mathfrak C_{\mathrm{aff}}$.

\item \textbf{$\beta\gamma$ system} is of contact/quartic type:
\[
\Theta_{\beta\gamma}^{\le 4}=H_{\beta\gamma}
+\mathfrak Q_{\beta\gamma},
\]
with quartic boundary term propagated from the local quartic vertex.
\end{enumerate}
Virasoro and $\mathcal{W}_N$ ($N\ge 3$) are the first genuinely mixed
families, with
\[
\Theta_{\mathrm{Vir}}^{\le 4}
=H_{\mathrm{Vir}}+\mathfrak C_{\mathrm{Vir}}
+\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}},
\qquad
\Theta_{W_N}^{\le 4}
=H_{W_N}+\mathfrak C^{\mathrm{grav}}_{W_N}
+\mathfrak Q^{\mathrm{contact}}_{W_N}.
\]
The coexistence of cubic and quartic local vertices is the source of
genuinely new modular phenomena (Theorems~\ref{thm:w-virasoro-quintic-forced}
and~\ref{thm:w-finite-termination} below).
\end{theorem}

\begin{proof}
The Heisenberg shadow is exactly quadratic because all OPE poles are of
order~$2$ and no composite fields appear
(Chapter~\ref{chap:free-fields}).  The affine shadow has a cubic
sector from $J_{(0)}J=[J,J]$ but no quartic contact term because the
OPE poles reach only order~$2$, and the Jacobiator absorbs the putative
quartic boundary.  The $\beta\gamma$ system has no cubic sector
($\mathfrak C_{\beta\gamma}=0$) but the fourth-order pole in
$\beta(z)\gamma(w)\sim (z-w)^{-1}$ combined with the normal-ordered
composite ${:}\beta\gamma{:}$ produces a nonzero quartic contact term.

For Virasoro, both mechanisms are present:
$T_{(1)}T=2T$ produces the cubic, and
$\Lambda_{\mathrm{Vir}}={:}TT{:}-\frac{3}{10}\partial^2T$ produces
the quartic contact (Theorem~\ref{thm:w-virasoro-mixed-shadow}).
The same reasoning extends to $\mathcal{W}_N$ via
Theorems~\ref{thm:w-principal-wn-hessian-cubic}
and~\ref{thm:w-principal-wn-contact-nonvanishing}.\qedhere
\end{proof}

\subsection{The Virasoro quintic and the infinite shadow tower}
\label{subsec:w-virasoro-quintic}

\begin{theorem}[Virasoro quintic forced; \ClaimStatusProvedHere]
\label{thm:w-virasoro-quintic-forced}
\index{shadow tower!Virasoro quintic}
On the Virasoro quartic shadow envelope
$E^{[4]}_{\mathrm{Vir}}$, the quintic obstruction is generically
nonzero:
\begin{equation}
\label{eq:w-virasoro-quintic-obstruction}
\mathfrak o_{\mathrm{Vir}}^{(5)}
=
\{\mathfrak C_{\mathrm{Vir}},
\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}}\}_{H_{\mathrm{Vir}}}
\neq 0
\qquad
\text{for generic $c$}.
\end{equation}
Consequently $\mathrm{Sh}_5(\mathrm{Vir})\neq 0$ generically: the
Virasoro shadow tower does not terminate at quartic order.
\end{theorem}

\begin{proof}
The gravitational cubic is $\mathfrak C_{\mathrm{Vir}}=2x^3$ and the
contact quartic is $\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}}=
Q_0\,x^4$ with $Q_0=10/[c(5c+22)]\neq 0$ for generic~$c$
(Theorem~\ref{thm:w-virasoro-quartic-explicit}).  Their single-edge
sewing contraction on the one-generator primary line with propagator
$P=2/c$ (inverse of the Hessian) is the $H$-Poisson bracket
\[
\{\mathfrak C_{\mathrm{Vir}},
\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}}\}_{H_{\mathrm{Vir}}}
=
\frac{\partial \mathfrak C}{\partial x}\cdot P\cdot
\frac{\partial \mathfrak Q}{\partial x}
=
6x^2 \cdot \frac{2}{c} \cdot 4Q_0 x^3
=
\frac{48Q_0}{c}\,x^5
\neq 0.
\]
By the all-arity master equation
(Theorem~\ref{thm:nms-all-arity-master-equation}),
$\nabla_H(\mathrm{Sh}_5)+\mathfrak o^{(5)}=0$, so
$\mathrm{Sh}_5\neq 0$.\qedhere
\end{proof}

\begin{remark}[Spectral curve interpretation of infinite depth]
\label{rem:virasoro-spectral-curve}
The infinite shadow tower of the Virasoro algebra reflects the spectral
correspondence of Theorem~\ref{thm:shadow-spectral-correspondence}
(Chapter~\ref{chap:arithmetic-shadows}): depth $= 3 + \dim S_k$, where
$S_k$ is the space of cusp forms, so the tower grows with
the cuspidal spectrum.  The self-referential OPE $T \in T_{(3)}T$
satisfies the criterion of Proposition~\ref{prop:self-referentiality-criterion},
forcing $r_{\max} = \infty$.
\end{remark}

\begin{corollary}[Explicit quintic shadow for Virasoro; \ClaimStatusProvedHere]
\label{cor:virasoro-quintic-shadow-explicit}
\index{shadow tower!quintic Virasoro formula}
The quintic shadow of the Virasoro algebra at central charge~$c$ is
\begin{equation}
\label{eq:virasoro-sh5-formula}
\mathrm{Sh}_5(\mathrm{Vir}_c)
\;=\;
-\frac{48}{c^2(5c+22)}\,x^5.
\end{equation}
The quintic shadow intensity $\rho_5 :=
|\mathrm{Sh}_5|/|\mathrm{Sh}_2|^{5/2}$ is
\begin{equation}
\label{eq:virasoro-quintic-intensity}
\rho_5(\mathrm{Vir}_c)
\;=\;
\frac{192\sqrt{2}}{c^{9/2}\,(5c+22)}.
\end{equation}
\end{corollary}

\begin{proof}
The all-arity master equation
$\nabla_H(\mathrm{Sh}_5) + \mathfrak{o}^{(5)} = 0$
gives $\mathrm{Sh}_5 = -\nabla_H^{-1}(\mathfrak{o}^{(5)})$.
On the single-generator primary line with Hessian
$H_{\mathrm{Vir}} = c/2$, the covariant derivative
$\nabla_H = (c/2)\partial_x$ and its inverse acts as
$\nabla_H^{-1}(f(x)) = (2/c)\int f$.  From
Theorem~\ref{thm:w-virasoro-quintic-forced}:
\[
\mathfrak{o}^{(5)}
= \frac{48 Q_0}{c}\,x^5
= \frac{48}{c}\cdot\frac{10}{c(5c+22)}\,x^5
= \frac{480}{c^2(5c+22)}\,x^5.
\]
The covariant derivative acts as $\nabla_H(S_r x^r) =
\{\kappa, S_r x^r\}_{H} = 2r\,S_r\, x^r$ on homogeneous
polynomials.  Therefore $\nabla_H^{-1}(\alpha\, x^r) =
\alpha/(2r)\,x^r$, giving
\[
\mathrm{Sh}_5
= -\frac{1}{2 \cdot 5}\cdot
\frac{480}{c^2(5c+22)}\,x^5
= -\frac{48}{c^2(5c+22)}\,x^5.
\]
The intensity normalizes against the quadratic shadow
$\mathrm{Sh}_2 = \kappa = c/2$:
$\rho_5 = |\mathrm{Sh}_5|/|\kappa|^{5/2}
= 48/[c^2(5c+22)] \cdot (2/c)^{5/2}
= 192\sqrt{2}/[c^{9/2}(5c+22)]$.
\end{proof}

\begin{theorem}[Virasoro shadow metric; \ClaimStatusProvedHere]
\label{thm:virasoro-shadow-generating-function}
\index{shadow tower!Virasoro generating function|textbf}
\index{Virasoro algebra!shadow generating function|textbf}
The shadow generating function
$H_{\mathrm{Vir}}(t,c) := \sum_{r=2}^{\infty} r\,\mathrm{Sh}_r(\mathrm{Vir}_c)\,t^r$
is algebraic of degree~$2$ over $\mathbb{Q}(c)[t]$
\textup{(}Remark~\textup{\ref{rem:shadow-algebraic-degree})}.
Explicitly, the shadow metric for $\mathrm{Vir}_c$ is
\begin{equation}\label{eq:virasoro-shadow-gf}
Q_{\mathrm{Vir}}(t) = c^2 + 12ct + \alpha(c)\,t^2,
\end{equation}
where the \emph{shadow control parameter} is
\begin{equation}\label{eq:virasoro-shadow-alpha}
\alpha(c) := \frac{180c + 872}{5c + 22}
= 36 + \frac{80}{5c+22},
\end{equation}
and the closed form is
\begin{equation}\label{eq:virasoro-shadow-gf-closed}
H_{\mathrm{Vir}}(t,c)
= t^2\sqrt{Q_{\mathrm{Vir}}(t)}
= t^2\sqrt{(c + 6t)^2 + \frac{80\,t^2}{5c+22}}.
\end{equation}
The radius of convergence is
\begin{equation}\label{eq:virasoro-shadow-gf-radius}
R(c) = c\sqrt{\frac{5c+22}{180c+872}},
\end{equation}
with poles only at $c = 0$ and
$c = -22/5$ \textup{(}Lee--Yang\textup{)} for all arities
\textup{(}\emph{pole purity}\textup{)}.
\end{theorem}

\begin{proof}
The shadow coefficients extracted from the recursive master
equation (Theorem~\ref{thm:nms-all-arity-master-equation})
through arity~$12$ are:
\begin{align*}
\mathrm{Sh}_2 &= \frac{c}{2}, &
\mathrm{Sh}_3 &= 2, &
\mathrm{Sh}_4 &= \frac{10}{c(5c+22)}, \\
\mathrm{Sh}_5 &= -\frac{48}{c^2(5c+22)}, &
\mathrm{Sh}_6 &= \frac{80(45c+193)}{3c^3(5c+22)^2}, &
\mathrm{Sh}_7 &= -\frac{2880(15c+61)}{7c^4(5c+22)^2}.
\end{align*}
Set $Q_{\mathrm{Vir}}(t) := c^2 + 12ct + \alpha(c)\,t^2$ and expand
$t^2\,Q_{\mathrm{Vir}}(t)^{1/2} = t^2\,c\,(1 + u)^{1/2}$ with
$u = 12t/c + \alpha t^2/c^2$.  The binomial expansion
$(1+u)^{1/2} = \sum_{n\geq 0}\binom{1/2}{n}u^n$
yields the coefficient of~$t^r$ as a polynomial in $\alpha/c^2$
and $12/c$.  At each arity $r = 2,\ldots,12$, matching
$r\,\mathrm{Sh}_r$ against the binomial coefficient determines
$\alpha(c)$ uniquely:
\begin{itemize}[nosep]
\item Arity~$2$: $H_2 = c$ gives $2\,\mathrm{Sh}_2 = c$, so
  $\mathrm{Sh}_2 = c/2$.
\item Arity~$3$: $H_3 = 6t$ gives $3\,\mathrm{Sh}_3 = 6$, matching the
  cubic $\mathfrak{C}_{\mathrm{Vir}} = 2x^3$.
\item Arity~$4$: $H_4 = (\alpha - 36)/(2c)$ gives
  $4\,\mathrm{Sh}_4 = (\alpha - 36)/(2c) = 40/[c(5c{+}22)]$,
  recovering the quartic contact
  (Theorem~\ref{thm:w-virasoro-quartic-explicit}).
\item Arities~$5$--$12$: verified by
  \texttt{compute/lib/virasoro\_shadow\_tower.py}.
\end{itemize}
To see that no further coefficients arise, write $H^2(t) = t^4\,P(t)$
and substitute into the recursive master equation at arity~$m$.
The MC recursion at arity $m \geq 5$ states
$\sum_{j+k=m+2} jk\,S_j\,S_k = -mc\,S_m$,
where $S_r := \mathrm{Sh}_r$.  This is exactly the condition
$[t^{m+2}](H^2) = 0$: the coefficient of $t^{m+2}$ in
$H^2 = (\sum_{r \geq 2} r\,S_r\, t^r)^2$ is
$\sum_{j+k=m+2} jk\,S_j\,S_k$, and the recursion identifies this
sum with $-mc\,S_m$.  But the contribution of
$[t^{m+2}](H^2)$ from the leading terms is
$2 \cdot m\,S_m \cdot 2\,S_2 + \text{(lower arities)}
= 2mc\,S_m + \text{(lower)}$,
which is exactly cancelled by the recursion to give
$[t^{m+2}](H^2) = 0$.  Hence $P(t)$ has degree~$\leq 2$, so
$H^2 = t^4\,Q_{\mathrm{Vir}}(t)$ with $Q_{\mathrm{Vir}}$
quadratic in~$t$, its three coefficients determined by
$\mathrm{Sh}_2$, $\mathrm{Sh}_3$, $\mathrm{Sh}_4$.
The algebraic relation $H^2 = t^4\,Q_{\mathrm{Vir}}(t)$ confirms
degree~$2$ over $\mathbb{Q}(c)[t]$
(Remark~\ref{rem:shadow-algebraic-degree}).
\end{proof}

\begin{remark}[Self-duality at $c = 13$]
\label{rem:virasoro-self-dual-shadow}
\index{Virasoro!self-dual shadow metric}
At the self-dual central charge $c = 13$: $Q_{\mathrm{Vir}}(t, 13) = 169 + 156t + \tfrac{3212}{87}\,t^2$ is invariant under $c \to 26{-}c$ (Koszul duality).  The shadow metric is a \emph{fixed point} of the Koszul involution.  The critical discriminant $\Delta(13) = 40/87$ satisfies $2\Delta(13) = 80/87$ (the complementarity sum at the self-dual point).  The spectral curve $\Sigma_{13}$ has a $\mathbb{Z}/2$-symmetry: the two sheets of the double cover are exchanged by the Koszul involution, and at $c = 13$ they coincide.
\end{remark}

\begin{remark}[Computational features of the Virasoro shadow metric]
\label{rem:virasoro-shadow-generating-function}
\index{shadow tower!Virasoro generating function}
The closed form~\eqref{eq:virasoro-shadow-gf-closed} exhibits
the following features specific to the Virasoro family:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Alternating signs.}
  For $r \geq 4$, the signs of $\mathrm{Sh}_r$ alternate.
  This follows from the binomial expansion of $(1+u)^{1/2}$
  with $\alpha - 36 = 80/(5c{+}22) > 0$: the deviation from
  perfect-square structure forces sign alternation.

\item \emph{Pole structure.}
  The denominator of $\mathrm{Sh}_r$ is
  $c^{r-3}(5c{+}22)^{\lfloor (r-2)/2 \rfloor}$, with poles at
  $c = 0$ and $c = -22/5$ (the Lee--Yang value).  Both poles
  originate from~$\alpha(c)$.

\item \emph{Discriminant.}
  $\Delta_Q = 144c^2 - 4\alpha c^2 = -320c^2/(5c{+}22) < 0$
  for $c > 0$.  Thus $Q_{\mathrm{Vir}}(t)$ is irreducible
  over~$\mathbb{R}$ and $H_{\mathrm{Vir}}$ is genuinely irrational.

\item \emph{Semiclassical limit.}
  As $c \to \infty$, $\alpha \to 36$,
  $Q_{\mathrm{Vir}} \to (c+6t)^2$, and the tower collapses to
  the Gaussian class~$\mathbf{G}$.
\end{enumerate}
\end{remark}

\begin{remark}[Shadow growth rate and convergence regime]
\label{rem:virasoro-shadow-growth-rate}
\index{shadow growth rate!Virasoro|textbf}
\index{Virasoro!convergence regime}
The shadow growth rate
(Definition~\ref{def:shadow-growth-rate}) is
$\rho(\mathrm{Vir}_c)
= \sqrt{(180c{+}872)/((5c{+}22)\,c^2)}$,
the reciprocal of the convergence
radius~\eqref{eq:virasoro-shadow-gf-radius}.
From the branch-point product
(Definition~\ref{def:shadow-growth-rate}):
$\rho^2 = q_2/q_0 = \alpha(c)/c^2$.
The equation $\rho = 1$ is the cubic
$5c^3 + 22c^2 - 180c - 872 = 0$
(Corollary~\ref{cor:virasoro-shadow-radius}(ii))
with unique positive root
$c_\star \approx 6.125$.
The three shadow regimes for the Virasoro family
(Theorem~\ref{thm:koszul-exchange-regimes}, $K = 26$):
\begin{itemize}[nosep]
\item $c < 6.13$: divergent tower ($\rho > 1$);
  $\mathrm{Vir}_{26-c}$ convergent.
\item $6.13 < c < 19.87$: both $\mathrm{Vir}_c$
  and $\mathrm{Vir}_{26-c}$ convergent.
\item $c > 19.87$: convergent tower; $\mathrm{Vir}_{26-c}$
  divergent.
\end{itemize}
Every unitary minimal model ($c < 1$) has
$\rho > 6.24$: the shadow tower diverges and the
shadow--Epstein zeta requires algebraic continuation
(Remark~\ref{rem:arithmetic-threshold}).
The string-theoretic value $c = 26$ has
$\rho \approx 0.23$ (strongly convergent).

The near-alternation of
signs (Remark~\ref{rem:virasoro-shadow-generating-function}(i))
is quantified by the branch-point argument
$\arg(t_0)/\pi \in (0.91, 1)$, approaching~$1$ in the
semiclassical limit (Remark~\ref{rem:virasoro-shadow-generating-function}(iv)).  The exponent~$-5/2$ in the
asymptotics
$S_r \sim A\,\rho^r\,r^{-5/2}\cos(r\theta + \varphi)$
is universal (Theorem~\ref{thm:shadow-radius}(ii)):
it reflects the square-root singularity of~$\sqrt{Q_L}$ at
the branch points, not the specific Virasoro OPE data.
\end{remark}

\begin{remark}[Complementarity potential]
\label{rem:virasoro-complementarity-potential}
\index{complementarity potential!Virasoro}
The complementarity potential
$S_{\mathrm{Vir}}(x) = \sum_{r=2}^\infty \frac{1}{2r}\,
\mathrm{Sh}_r\,x^r$ through septic order is
\begin{align*}
S_{\mathrm{Vir}}(x)
&= \frac{c}{4}\,x^2
+ \frac{1}{3}\,x^3
+ \frac{5}{12\,c(5c{+}22)}\,x^4
- \frac{2}{5\,c^2(5c{+}22)}\,x^5 \\
&\quad + \frac{45c{+}193}{27\,c^3(5c{+}22)^2}\,x^6
- \frac{4(15c{+}61)}{49\,c^4(5c{+}22)^2}\,x^7
+ O(x^8).
\end{align*}
\end{remark}

\begin{theorem}[Finite termination for primitive archetypes; \ClaimStatusProvedHere]
\label{thm:w-finite-termination}
\index{shadow tower!finite termination}
For the three frame families, the shadow tower terminates at finite arity:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textbf{Heisenberg:} $\mathrm{Sh}_r(\mathcal H)=0$ for all
  $r\ge 3$.  The tower terminates at arity~$2$: it is exactly Gaussian.

\item \textbf{Affine $\widehat{\mathfrak{sl}}_2$
  \textup{(strict sector, minimal gauge):}}
  $\mathrm{Sh}_r(\mathrm{aff})=0$ for $r\ge 4$.  The tower terminates
  at arity~$3$.

\item \textbf{$\beta\gamma$ \textup{(weight-changing line):}}
  $\mathrm{Sh}_r(\beta\gamma)|_L=0$ for $r\ge 3$ by rank-one abelian
  rigidity.  The tower terminates at arity~$4$ on the
  weight-changing line.
\end{enumerate}
Virasoro is the first genuinely infinite tower:
$\mathrm{Sh}_r(\mathrm{Vir})\neq 0$ for all $r\ge 3$ for generic~$c$.
\end{theorem}

\begin{proof}
For each primitive archetype, finite termination follows from vanishing
of all obstruction sources at the relevant arity.  For the Heisenberg,
all higher brackets vanish (the OPE is quadratic, so no composite
fields appear).  For affine $\widehat{\mathfrak{sl}}_2$, the Jacobiator
vanishes and the quartic gauge freedom absorbs all remaining terms.
For $\beta\gamma$, rank-one abelian rigidity
(Theorem~\ref{thm:nms-rank-one-rigidity}) gives vanishing on the
rank-one weight-changing line.

For Virasoro, Theorem~\ref{thm:w-virasoro-quintic-forced} gives
$\mathrm{Sh}_5\neq 0$.  Then $\mathfrak o^{(6)}$ contains
$\{\mathfrak C,\mathrm{Sh}_5\}\neq 0$, forcing
$\mathrm{Sh}_6\neq 0$, and so on by induction: the cubic vertex
$\mathfrak C=2x^3$ acts as a permanent source, and the non-polynomial
character of the complementarity potential is established.\qedhere
\end{proof}

\begin{remark}[Shadow Postnikov tower interpretation]
\label{rem:w-postnikov-interpretation}
\index{shadow Postnikov tower!archetype classification}
Theorem~\ref{thm:w-finite-termination} classifies the
shadow Postnikov tower
(Definition~\ref{def:shadow-postnikov-tower}) into
four archetype classes:
\begin{center}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{llll}
\toprule
\emph{Archetype} & \emph{Termination arity} &
\emph{Obstruction mechanism} & \emph{Tower type} \\
\midrule
Heisenberg & $2$ (Gaussian) & no higher operations &
exact quadratic \\
Affine & $3$ (Lie) & Jacobi identity &
quadratic + cubic \\
$\beta\gamma$ & $4$ (contact) & rank-one rigidity &
quartic on weight line \\
Virasoro/$\mathcal{W}_N$ & $\infty$ & permanent cubic source &
non-polynomial \\
\bottomrule
\end{tabular}
\end{center}
For families with infinite towers, the shadow Postnikov
tower does not converge at any finite arity: the full
limit $\Theta_\cA = \varprojlim_r
\Theta_\cA^{\leq r}$
(Theorem~\ref{thm:recursive-existence}) is genuinely
infinite-order.  This is the mathematical content of the
statement that the Virasoro complementarity potential is
non-polynomial.
\end{remark}

\begin{corollary}[Virasoro/$\mathcal{W}_N$ shadow Postnikov tower:
infinite; \ClaimStatusProvedHere]
\label{cor:virasoro-postnikov-nontermination}
\index{shadow Postnikov tower!Virasoro non-termination}
The shadow Postnikov tower
\textup{(}Definition~\textup{\ref{def:shadow-postnikov-tower})}
of the Virasoro algebra \textup{(}and principal
$\mathcal{W}_N$ for $N \geq 2$\textup{)} does not terminate at
any finite arity:
$o_{r+1}(\mathrm{Vir}) \neq 0$ for all $r \geq 4$ for
generic~$c$.
Equivalently, $\Theta_{\mathrm{Vir}}^{\leq r} \neq
\Theta_{\mathrm{Vir}}^{\leq r-1}$ for all $r \geq 3$.
The permanent cubic source $\mathfrak{C}_{\mathrm{Vir}} = 2x^3$
drives the infinite tower.
\end{corollary}

\begin{proof}
Immediate from Theorems~\ref{thm:w-virasoro-quintic-forced}
and~\ref{thm:w-finite-termination}: the inductive mechanism
$\mathfrak{o}^{(r+1)} \ni
\{\mathfrak{C},\mathrm{Sh}_r\}_H \neq 0$
propagates non-vanishing to all arities.
\end{proof}

\subsection{Genus-$1$ Hessian correction for the Virasoro shadow}
\label{subsec:w-virasoro-genus1-hessian}
\index{genus loop operator!Virasoro computation}
\index{Hessian correction!genus-1 Virasoro}

The infinite shadow tower carries information beyond the
$\hat{A}$-genus.  The first concrete manifestation is the genus-$1$
Hessian correction obtained by applying the genus loop operator
$\Lambda_P$ (Definition~\ref{def:nms-genus-loop-operator}) to the
quartic shadow.  We give the self-contained computation here;
the abstract framework is developed in
Appendix~\ref{sec:nms-genus-loop-operator}.

\begin{theorem}[Genus-$1$ Hessian correction for Virasoro;
\ClaimStatusProvedHere]
\label{thm:w-virasoro-genus1-hessian}
\index{Virasoro algebra!genus-1 Hessian correction}
On the primary line with $H = (c/2)x^2$,
$\mathfrak C = 2x^3$,
$\mathfrak Q^{\mathrm{contact}} = Q_0\,x^4$ where
$Q_0 = 10/[c(5c+22)]$, one has:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The genus-$1$ Hessian correction is
\begin{equation}
\label{eq:w-virasoro-genus1-hessian}
\delta H^{(1)}_{\mathrm{Vir}}
= \Lambda_P\bigl(\mathfrak Q^{\mathrm{contact}}_{\mathrm{Vir}}\bigr)
= \frac{120}{c^2(5c+22)}\,x^2.
\end{equation}

\item The genus-$1$ loop ratio is
\begin{equation}
\label{eq:w-virasoro-loop-ratio}
\rho^{(1)}_{\mathrm{Vir}}
:= \frac{\delta H^{(1)}_{\mathrm{Vir}}}{H^{(0)}_{\mathrm{Vir}}}
= \frac{240}{c^3(5c+22)}.
\end{equation}
This is a nontrivial rational function of $c$ that is not
determined by $\kappa = c/2$ alone.  Two algebras with the same
$\kappa$ but different $c$ are distinguished by
$\rho^{(1)}$.
\end{enumerate}
\end{theorem}

\begin{proof}
The computation proceeds in five steps.

\emph{Step~1} (Genus loop on rank-$1$ symmetric tensors).
On a one-dimensional primary slice $V = \mathbb C\langle x\rangle$
with Hessian $H = (c/2)x^2$, the propagator is $P = 2/c$.
The genus loop operator
$\Lambda_P \colon \operatorname{Sym}^r(V^*) \to
\operatorname{Sym}^{r-2}(V^*)$
contracts two symmetric legs with the propagator
(Definition~\ref{def:nms-genus-loop-operator}).  For a
rank-$r$ symmetric tensor $\alpha = \alpha_0\,x^r$, the
number of ways to choose the two legs to contract is
$\binom{r}{2}$, giving
\begin{equation}
\label{eq:w-genus-loop-rank1-formula}
\Lambda_P(\alpha_0\,x^r)
= \binom{r}{2} \cdot P \cdot \alpha_0 \cdot x^{r-2}.
\end{equation}

\emph{Step~2} (Apply to the quartic shadow).
With $r = 4$, $\alpha_0 = Q_0 = 10/[c(5c+22)]$, and
$P = 2/c$:
\[
\Lambda_P(Q_0\,x^4)
= \binom{4}{2} \cdot \frac{2}{c} \cdot
\frac{10}{c(5c+22)} \cdot x^2
= 6 \cdot \frac{2}{c} \cdot
\frac{10}{c(5c+22)} \cdot x^2
= \frac{120}{c^2(5c+22)}\,x^2.
\]

\emph{Step~3} (Identify the genus-$1$ Hessian correction).
By the non-separating clutching law
(Corollary~\ref{cor:nms-genus-one-hessian-correction}),
the genus-$1$ correction to the Hessian in the one-vertex
sector is $\delta H^{(1)} = \Lambda_P(\mathfrak Q^{(0)})$.
Thus
\[
\delta H^{(1)}_{\mathrm{Vir}}
= \frac{120}{c^2(5c+22)}\,x^2.
\]

\emph{Step~4} (Compute the loop ratio).
\[
\rho^{(1)}_{\mathrm{Vir}}
= \frac{\delta H^{(1)}_{\mathrm{Vir}}}{H^{(0)}_{\mathrm{Vir}}}
= \frac{120/[c^2(5c+22)] \cdot x^2}{(c/2)\,x^2}
= \frac{120}{c^2(5c+22)} \cdot \frac{2}{c}
= \frac{240}{c^3(5c+22)}.
\]

\emph{Step~5} (Apply to the cubic shadow).
With $r = 3$, $\alpha_0 = 2$, and $P = 2/c$:
\begin{equation}
\label{eq:w-virasoro-cubic-loop-computation}
\Lambda_P(\mathfrak C_{\mathrm{Vir}})
= \Lambda_P(2x^3)
= \binom{3}{2} \cdot \frac{2}{c} \cdot 2 \cdot x
= \frac{12}{c}\,x.
\end{equation}
This is the genus-$1$ correction to the linear term: a canonical
direction in $V^*$ determined by the cubic shadow and the
propagator.  It is the rank-$1$ analogue of the Weyl vector
direction detected by the affine cubic loop
(Theorem~\ref{thm:nms-genus-loop-model-families}(ii)).\qedhere
\end{proof}

\begin{remark}[Tensorial vs.\ scalar modular invariants]
\label{rem:w-virasoro-tensorial-invariant}
\index{modular invariant!tensorial}
The genus-$1$ Hessian correction
$\delta H^{(1)}_{\mathrm{Vir}} = 120/[c^2(5c+22)] \cdot x^2$
is a \emph{tensorial} modular invariant: it lives in
$\operatorname{Sym}^2(V^*)$ and is not determined by the scalar
curvature $\kappa = c/2$.  In particular, consider two hypothetical
chiral algebras $\cA$ and $\cA'$ with
$\kappa(\cA) = \kappa(\cA') = c/2$ but whose quartic contact
coefficients differ.  Then
$\delta H^{(1)}_{\cA} \neq \delta H^{(1)}_{\cA'}$:
the genus-$1$ modular homotopy theory distinguishes them even
though their $\hat{A}$-genera agree.  The loop ratio
$\rho^{(1)} = 240/[c^3(5c+22)]$ is the simplest numerical
invariant extracted from this tensorial data.
\end{remark}

\begin{remark}[The infinite tower and modular information beyond
the $\hat{A}$-genus]
\label{rem:w-infinite-tower-beyond-ahat}
\index{shadow tower!infinite!modular information}
\index{A-hat genus@$\hat{A}$-genus!limitations}
Theorem~\ref{thm:w-finite-termination} reveals a fundamental structural
divide.  The primitive archetypes terminate: Gaussian at arity~$2$,
Lie/tree at arity~$3$, contact at arity~$4$.  Their complementarity
potentials $S_{\cA}$ are polynomial, and the information they encode
about the moduli space $\overline{\mathcal{M}}_{g,n}$ is captured by
finitely many tautological classes.

Virasoro is different.  The non-polynomial complementarity potential
$S_{\mathrm{Vir}}$ records an infinite sequence of tautological
invariants $\mathrm{Sh}_r(\mathrm{Vir})$ for $r=2,3,4,5,\dots$,
each capturing finer modular structure than the last.  This is the
mechanism by which the Virasoro modular package carries strictly more
information than the $\hat{A}$-genus: the $\hat{A}$-genus is
controlled by the scalar curvature $\kappa$ (arity~$2$) and a finite
number of Pontryagin-type corrections, whereas
$\Theta_{\mathrm{Vir}}$ encodes an infinite tower of genuinely new
invariants sourced by the cubic--quartic interaction.

More precisely, the all-arity master equation
\[
\nabla_{H_{\mathrm{Vir}}}(\mathrm{Sh}_r)
+\mathfrak o^{(r)}=0
\]
ensures that each $\mathrm{Sh}_r$ is determined by the lower-arity
data via the Poisson bracket with $\mathfrak C$ and
$\mathfrak Q^{\mathrm{contact}}$.  The recursion never terminates
because $\mathfrak C\neq 0$ and $\mathfrak Q^{\mathrm{contact}}\neq 0$
simultaneously --- the hallmark of a mixed family.  The same mechanism
applies to all principal $\mathcal{W}_N$ with $N\ge 3$
(Theorem~\ref{thm:w-principal-wn-contact-nonvanishing}), producing an
infinite tower for every member of the $\mathcal{W}$-algebra series.
\end{remark}

\subsection{The \texorpdfstring{$\mathcal{W}_3$}{W3} quintic obstruction}
\label{subsec:w-w3-quintic-obstruction}
\index{quintic obstruction!W3@$\mathcal{W}_3$}
\index{shadow tower!W3 infinite@$\mathcal{W}_3$ infinite}

The Virasoro quintic was forced by the interaction between the
rank-$1$ cubic $\mathfrak C = 2x^3$ and the rank-$1$ quartic
$\mathfrak Q = Q_0\,x^4$
(Theorem~\ref{thm:w-virasoro-quintic-forced}).  For $\mathcal{W}_3$
the mechanism is richer: the two-generator primary slice supports
genuinely multi-variable obstructions.

\begin{proposition}[$\mathcal{W}_3$ quintic obstruction;
\ClaimStatusProvedHere]
\label{prop:w-w3-quintic-obstruction}
\index{W3@$\mathcal{W}_3$!quintic obstruction}
On the two-generator primary slice of $\mathcal{W}_3$ with
coordinates $(t,w)$ dual to $(T,W)$, the quintic obstruction is
\begin{equation}
\label{eq:w-w3-quintic-obstruction}
\mathfrak o^{(5)}_{W_3}
= \bigl\{\mathfrak C_{W_3},\,
\mathfrak Q_{W_3}\bigr\}_{H_{W_3}}
\neq 0
\qquad\text{for generic~$c$}.
\end{equation}
Consequently $\mathrm{Sh}_5(\mathcal{W}_3) \neq 0$ generically:
the $\mathcal{W}_3$ shadow tower is also infinite.
\end{proposition}

\begin{proof}
The cubic $\mathfrak C_{W_3} = 2t^3 + 3tw^2$
(Theorem~\ref{thm:w-w3-mixed-shadow}) is a nonzero polynomial of
degree~$3$ in $(t,w)$.  The quartic $\mathfrak Q_{W_3}$ contains
the weight-$4$ contact channel through~$\Lambda$ with coefficient
proportional to $32/(22+5c)$ as well as weight-$6$ contact
channels through $\Lambda_2$ and $\Lambda_3$.  In particular,
$\mathfrak Q_{W_3}\neq 0$ for generic~$c$.

The $H$-Poisson bracket on the primary slice with diagonal
propagator $P = \operatorname{diag}(2/c,\,3/c)$ is
\[
\bigl\{\mathfrak C,\,\mathfrak Q\bigr\}_{H}
= \frac{\partial\mathfrak C}{\partial t}\cdot \frac{2}{c}\cdot
\frac{\partial\mathfrak Q}{\partial t}
+ \frac{\partial\mathfrak C}{\partial w}\cdot \frac{3}{c}\cdot
\frac{\partial\mathfrak Q}{\partial w}.
\]
Since $\partial\mathfrak C/\partial t = 6t^2 + 3w^2$ and
$\partial\mathfrak C/\partial w = 6tw$, and the quartic gradients
are generically nonzero, the bracket is a degree-$5$ polynomial
in $(t,w)$ that does not vanish identically.  By the all-arity
master equation
(Theorem~\ref{thm:nms-all-arity-master-equation}),
$\nabla_H(\mathrm{Sh}_5) + \mathfrak o^{(5)} = 0$,
so $\mathrm{Sh}_5 \neq 0$.\qedhere
\end{proof}

\begin{remark}[$\mathcal{W}_3$ multi-channel tower: T-line autonomy and mixing]
\label{rem:w3-multi-channel-tower}
\index{W3@$\mathcal{W}_3$!T-line autonomy}
\index{W3@$\mathcal{W}_3$!mixing polynomial}
The $\mathcal{W}_3$ shadow tower on the $T$-line
($w = 0$, only stress-tensor insertions) is \emph{autonomous}:
it equals the single-variable Virasoro tower of
Theorem~\ref{thm:virasoro-shadow-generating-function} exactly,
verified through arity~$10$.  The mechanism is that the $W$-line
alternating vanishing
(Corollary~\ref{cor:w-line-alternating-vanishing}) kills all
odd-$W$-leg contributions, and the even-$W$-leg terms decouple on
$w = 0$.

The \emph{mixing polynomial} (computational data from Proposition~\ref{thm:propagator-variance})
\begin{equation}\label{eq:w3-mixing-polynomial}
P(c) = 25c^2 + 100c - 428 = 25(c+2)^2 - 528
\end{equation}
controls arity-$6$ non-autonomy on the mixed lines.
Proposition~\ref{thm:propagator-variance} gives
$\delta(\mathcal{W}_3) = 0$ if and only if $P(c) = 0$, i.e.\
at $c = (-100 \pm \sqrt{100^2 + 4\cdot 25\cdot 428})/(2\cdot 25)
= -2 \pm 2\sqrt{132/25}$.
At these curvature-proportionality loci the multi-channel tower
collapses to a single effective channel at arity~$6$; for all other~$c$ the
$T$--$W$ mixing is irreducible and the diagonal tower differs from
the autonomous Virasoro tower starting at arity~$6$.

The $\mathcal{W}_3$ quintic nonvanishing
(Theorem~\ref{thm:w3-quintic-nonvanishing}) confirms that
$\mathcal{W}_3$ belongs to class~M ($r_{\max} = \infty$), matching
the Virasoro classification but with a richer multi-variable structure.
\end{remark}

\begin{example}[$\mathcal{W}_3$ shadow tower coefficients]
\label{ex:w3-shadow-coefficients}
\index{$\mathcal{W}_3$!shadow tower coefficients}
The two-channel shadow tower for $\mathcal{W}_3$ with generators $T$ (weight~$2$) and $W$ (weight~$3$), computed through arity~$6$ (\texttt{coxeter\_arity4\_deep.py}, $69$~tests):
\begin{center}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{cl}
\toprule
$r$ & $\mathrm{Sh}_r(x_T, x_W)$ \\
\midrule
$2$ & $\frac{c}{2}\,x_T^2 + \frac{c}{3}\,x_W^2$ \\[4pt]
$3$ & $2\,x_T^3 + 3\,x_T\,x_W^2$ \\[4pt]
$4$ & $\frac{10}{c(5c{+}22)}\,x_T^4 + \frac{960}{c(5c{+}22)^2}\,x_T^2 x_W^2 + \frac{2560}{c(5c{+}22)^3}\,x_W^4$ \\[4pt]
$5$ & $\frac{-48}{c^2(5c{+}22)}\,x_T^5
      - \frac{24(5c{+}262)}{c^2(5c{+}22)^2}\,x_T^3 x_W^2
      - \frac{1152(5c{+}38)}{c^2(5c{+}22)^3}\,x_T x_W^4$ \\[4pt]
$6$ & $\frac{80(45c{+}193)}{3c^3(5c{+}22)^2}\,x_T^6
      + \dotsb
      + \frac{64(5625c^4{+}117000c^3{+}\dotsb)}{c^3(5c{+}22)^6}\,x_W^6$ \\
\bottomrule
\end{tabular}
\end{center}
\noindent
The $T$-line restriction ($x_W = 0$) equals the Virasoro shadow tower identically at all computed arities (verified through $r = 10$).  Odd powers of $x_W$ vanish by $W$-parity.  The full $2$-D tower is computed through arity~$8$ ($21$~nonzero coefficients, each a closed-form rational function of~$c$).  All denominators factor as $c^a(5c{+}22)^b$: the Kac-shadow singularity principle holds on the full $2$-D deformation space, not just on~$1$-D projections.  The mixed coefficients (those with $x_T^a x_W^b$ for $0 < a, b$) are the genuinely new data invisible on either~$1$-D projection.
\end{example}

\begin{remark}[Coxeter anomaly]
\label{rem:coxeter-anomaly}
\index{Coxeter anomaly|textbf}
\index{$\mathcal{W}_3$!Coxeter anomaly}
The naive two-channel sewing of the cubic shadow (using only $T_{(1)}T = 2T$ and $T_{(1)}W = 3W$) predicts a quartic $S_4^{\mathrm{free}} = -9/(2c)$ on the $T$-line, missing the factor $(5c{+}22)$ in the denominator.  The actual quartic $10/[c(5c{+}22)]$ arises from the composite operator $\Lambda = {:}TT{:} - \tfrac{3}{10}\partial^2 T$ at conformal weight~$4$, whose exchange produces the Kac-determinant factor.  The difference $(45c{+}218)/[2c(5c{+}22)]$ is the \emph{Coxeter anomaly}: the quartic contact contribution from composite operators not captured by the strong-generator OPE alone.
\end{remark}

\begin{remark}[$\mathcal{W}_3$ $W$-line structure and inter-channel coupling]
\label{rem:w3-w-line}
\label{rem:w3-interchannel-coupling}
\index{$\mathcal{W}_3$!$W$-line shadow}
\index{inter-channel coupling|textbf}
\index{shadow tower!inter-channel coupling}
On the $W$-line ($x_T = 0$): $\mathrm{Sh}_r = 0$ for odd~$r$ ($W$-parity).  The even-arity tower $S_2^W = c/3$, $S_4^W = 2560/[c(5c{+}22)^3]$ does \emph{not} follow the single-line $\sqrt{Q}$ structure (Theorem~\ref{thm:riccati-algebraicity}): the $W$-line is non-autonomous, receiving backreaction from the $T$-channel through cross-derivatives in the $2$-D H-Poisson bracket.  This contrasts with the exact autonomy of the $T$-line.

\medskip\noindent\emph{Inter-channel coupling mechanism.}\;
At arity~$6$ the obstruction on the $W$-line receives a $T$-channel correction
absent from the autonomous $1$-D recursion.
The cubic shadow $\mathrm{Sh}_3 = 2x_T^3 + 3x_T x_W^2$ has
$(\partial_{x_T} \mathrm{Sh}_3)|_{x_T = 0} = 3 x_W^2 \neq 0$:
it has a nonvanishing \emph{normal derivative} on the $W$-line.
The quintic shadow $\mathrm{Sh}_5$ has an $(x_T^1 x_W^4)$-component
$S_{1,4} = -1152(5c{+}38)/[c^2(5c{+}22)^3]$ whose normal derivative
is $S_{1,4}\,x_W^4$.  The $T$-channel bracket
$\{\mathrm{Sh}_3,\mathrm{Sh}_5\}^T|_{x_T = 0} = (3x_W^2)(2/c)(S_{1,4}\,x_W^4)$
contributes an arity-$6$ correction
\begin{equation}
\label{eq:w3-interchannel-correction}
  \delta_6^{W\text{-line}}
  \;=\;
  \frac{576(5c+38)}{c^3(5c+22)^3}
\end{equation}
to the $W$-line sextic shadow, shifting it from the autonomous value $-13107200/[c^3(5c{+}22)^6]$ to the full value.  The autonomous $W$-line recursion misses this entirely.  At arity~$8$ and higher, further $T$-channel corrections enter through $\{\mathrm{Sh}_3, \mathrm{Sh}_7\}^T$, $\{\mathrm{Sh}_5, \mathrm{Sh}_5\}^T$, etc.

The coupling correction~\eqref{eq:w3-interchannel-correction} vanishes on any direction~$L$ in the deformation space where the propagator variance $\delta_{\mathrm{mix}} = 0$ (Proposition~\ref{thm:propagator-variance}).  The $T$-line is autonomous precisely because it has no transverse normal derivatives to couple to.  More generally, a subline of the deformation space is autonomous at arity~$6$ if and only if it lies in the kernel of the propagator variance form.
\end{remark}

%% ---------------------------------------------------------------
\section{The \texorpdfstring{$N\!=\!1$}{N=1} super-Virasoro PVA and 3d supergravity}
\label{sec:super-virasoro-pva}
\index{super-Virasoro algebra!PVA}
\index{supergravity!3d holomorphic-topological}

The Virasoro PVA of
\S\ref{subsec:virasoro-teichmuller-phase-space} admits an $N=1$
supersymmetric extension.  The associated 3d theory is a
holomorphic-topological supergravity.

\begin{definition}[$N=1$ super-Virasoro PVA;
\ClaimStatusProvedElsewhere{} \cite{KhanZeng25}]
\label{def:super-virasoro-pva}
\index{super-Virasoro algebra!lambda-bracket@$\lambda$-bracket}
The \emph{$N=1$ super-Virasoro Poisson vertex algebra} is
\begin{equation}\label{eq:super-vir-pva}
\mathcal{P}_{\mathrm{sVir}}
= \operatorname{Sym}\!\bigl(\mathbb{C}[\partial]T
  \oplus \mathbb{C}[\partial]G\bigr),
\end{equation}
where $T$ has conformal weight~$2$ (stress tensor) and $G$ has
weight~$\tfrac{3}{2}$ (supercurrent), with $\lambda$-brackets
\begin{align}
\{T_\lambda T\}
  &= \partial T + 2T\lambda + \tfrac{c}{12}\lambda^3,
  \label{eq:svir-TT}\\
\{T_\lambda G\}
  &= \partial G + \tfrac{3}{2}\,G\lambda,
  \label{eq:svir-TG}\\
\{G_\lambda G\}
  &= 2T + \tfrac{c}{3}\lambda^2.
  \label{eq:svir-GG}
\end{align}
The bracket $\{G_\lambda G\} = 2T + \frac{c}{3}\lambda^2$ is the
classical $\lambda$-bracket encoding: the stress tensor is the
square of the supercurrent.
\end{definition}

\begin{proposition}[3d HT supergravity action;
\ClaimStatusConjectured]
\label{prop:super-virasoro-3d-action}
\index{supergravity!3d HT action}
The 3d holomorphic-topological supergravity associated to
$\mathcal{P}_{\mathrm{sVir}}$ has fields $(\mu,T)$ of spins
$(2,-1)$ and $(\chi,G)$ of spins $(\frac{3}{2},-\frac{1}{2})$ on
$M = \mathbb{R}_t \times \Sigma$, with action
\begin{multline}\label{eq:super-virasoro-3d-action}
  S_{\mathrm{sVir}}
  \;=\;
  \int \mu\,(dt + \bar\partial)\,T
  \;+\;
  \chi\,(dt + \bar\partial)\,G \\
  +\;\int\!\Bigl(
    T\mu\partial\mu
    + \tfrac{c}{24}\,\mu\,\partial^3\mu
    + \tfrac{3}{2}\,G\chi\partial\mu
    + (\partial G)\chi\mu
    + 2T\chi^2
    + \tfrac{c}{3}\,\chi\,\partial^2\chi
  \Bigr).
\end{multline}
The supercurrent coupling $2T\chi^2$ and the gravitino kinetic
correction $\frac{c}{3}\chi\partial^2\chi$ are read off from the
$\{G_\lambda G\}$ bracket~\eqref{eq:svir-GG} by the standard
Poisson-sigma-model dictionary of~\cite{KhanZeng25}.
\end{proposition}

\begin{remark}[Slab reduction and supersymmetric central-charge shift]
\label{rem:super-vir-slab-reduction}
\index{slab reduction!super-Virasoro}
\index{central charge!supersymmetric shift}
Under slab reduction, the super-Virasoro theory decomposes into a
spin-$(2,-1)$ $\beta\gamma$ system ($c(2) = 26$ by
equation~\eqref{eq:w3-central-charge-formula}) and a
spin-$(\frac{3}{2},-\frac{1}{2})$ $\beta\gamma$ system
($c(\frac{3}{2}) = 11$), giving $c_{\mathrm{slab}} = 37$.  The quantum
$N=1$ super-Virasoro algebra appears at the shifted central charge
\begin{equation}\label{eq:svir-ceff}
  c_{\mathrm{eff}} = c + \tfrac{37}{2}.
\end{equation}
The complementarity pairing for the super-Virasoro algebra
is $c + c' = 37$, the supersymmetric analogue of the bosonic
Virasoro pairing $c + c' = 26$.
\end{remark}

\begin{remark}[Supersymmetric shadow tower]
\label{rem:super-virasoro-shadow-tower}
\index{shadow tower!super-Virasoro}
The shadow tower of the $N=1$ super-Virasoro algebra inherits a
$\mathbb{Z}/2$-grading from the supercurrent~$G$.  The bracket
$\{G_\lambda G\} = 2T + \frac{c}{3}\lambda^2$ ensures that the
gravitino sector does not generate independent quartic obstructions:
the quartic contact invariant
$Q^{\mathrm{contact}}_{\mathrm{sVir}}$ factorises through the
bosonic Virasoro quartic of
\S\ref{subsec:w-virasoro-quartic-explicit}.  This is the
shadow-calculus manifestation of supersymmetric non-renormalization.
The $N=1$ extension amounts to
enlarging the graph-sum data of
$\Theta_{\mathrm{Vir}_c}$~\eqref{eq:modular-bar-hamiltonian} by
half-integer-spin propagators $P_G$ for the supercurrent; the
supersymmetric Ward identity forces the $G$-channel graphs to
factor through the $T$-channel, preserving the projection structure
of Remark~\ref{rem:five-from-one}.
\end{remark}


%% ---------------------------------------------------------------
\section{Semistrict modular higher-spin geometry}
\label{sec:semistrict-modular-higher-spin}
\index{semistrictity!higher-spin geometry}
\index{W-algebra@$\mathcal{W}$-algebra!semistrict envelope}

The Virasoro shadow tower is infinite
(Theorem~\ref{thm:w-virasoro-quintic-forced}): the quintic
obstruction is nonzero, and so is every subsequent order
generically.  One might therefore expect that the \emph{bulk}
deformation algebra controlling the $\mathcal{W}_3$ sector is
equally wild --- an infinite sequence of higher operations $\ell_n$
with no structural simplification.  The truth is the reverse.  The
classical $\mathcal{W}_3$ Poisson vertex
algebra~\eqref{eq:w3-pva} has nonlinear generator-degree exactly
two: the only non-polynomial coefficient in the $\lambda$-brackets
is the $T^2$ term in $\{W_\lambda W\}$, which is quadratic in
generators.  The associated three-dimensional
holomorphic-topological Poisson sigma model therefore has a BV
differential that terminates at cubic order.  The resulting cyclic
$L_\infty$-algebra has $\ell_n = 0$ for $n \ge 4$.  This is
semistrictity: an infinite shadow tower generated by a
\emph{finite-arity} bulk.

The paradox is precise and structurally loaded.  The shadow tower
records the nonlinear deformation theory of a moduli problem
organized by graph sums with arbitrarily many vertices.  When the
bulk interaction has only two- and three-valent vertices, a single
trivalent graph can be iterated to produce arbitrarily high contact
orders --- but the local interaction data at each vertex remains
ternary.  The infinite tower is not a consequence of infinite
interaction complexity; it is a consequence of iterated
\emph{finite} complexity.  This is the structural mechanism behind
every ``higher-spin gravity is finite-valent at each vertex but
infinite in diagram count'' statement in the physics literature.

\subsection{Nonlinear generator-degree and finite-arity theorems}
\label{subsec:semistrict-finite-arity}

\begin{definition}[Nonlinear generator-degree]
\label{def:w-nonlinear-generator-degree}
\index{nonlinear generator-degree}
Let $V$ be a freely generated Poisson vertex algebra on generators
$u_i$.  The \emph{nonlinear generator-degree} of~$V$ is the maximal
number of generator factors appearing in any monomial of any
$\lambda$-bracket coefficient $\{u_i{}_\lambda u_j\}$, taken over all
pairs $(i,j)$.
\end{definition}

\begin{definition}[Higher-spin envelope]
\label{def:w-higher-spin-envelope}
\index{higher-spin envelope}
Let $V$ be a freely generated Poisson vertex algebra, and let
$\mathfrak{M}_V$ be the formal moduli problem at the vacuum of the
three-dimensional holomorphic-topological Poisson sigma model
attached to~$V$.  Write
\[
Q_{\mathrm{BV}} = \sum_{n \ge 1} Q_n
\]
for the Taylor expansion of the BV homological vector field into
homogeneous polynomial components of degree~$n$.  The
\emph{higher-spin envelope} of~$V$ is the completed cyclic
$L_\infty$-algebra
\[
\operatorname{HS}(V)
\]
whose $n$-ary bracket $\ell_n$ is the shifted multilinear operation
corresponding to~$Q_n$.
\end{definition}

\begin{theorem}[Finite-arity theorem for polynomial PVAs;
\ClaimStatusProvedHere]
\label{thm:w-finite-arity-polynomial-pva}
\index{finite-arity theorem!polynomial PVA}
Let $V$ be a freely generated Poisson vertex algebra of nonlinear
generator-degree at most~$d$.  Then $\operatorname{HS}(V)$ is a
completed cyclic $L_\infty$-algebra with
\[
\ell_n = 0 \qquad \text{for all } n > d+1.
\]
\end{theorem}

\begin{proof}
The BV differential of the associated Poisson sigma model has the
schematic form
\[
Q_{\mathrm{BV}}\Phi^i
= d_{\mathrm{HT}}\Phi^i + \Pi^{ij}(\partial,\Phi)\,\eta_j,
\qquad
Q_{\mathrm{BV}}\eta_i
= d_{\mathrm{HT}}\eta_i
+ \tfrac{1}{2}\sum_{n \ge 0}(-\partial)^n \eta_j\,
\frac{\partial\Pi^{jk}(\partial,\Phi)}{\partial(\partial^n\Phi^i)}\,\eta_k,
\]
where $\Pi$ records the $\lambda$-bracket coefficients of~$V$; compare
\cite[\S3]{KhanZeng25}.  If every coefficient of~$\Pi$ has nonlinear
generator-degree at most~$d$, then the first formula is polynomial of
total degree at most $d+1$: a degree-$\le d$ coefficient multiplies
one ghost~$\eta_j$.  In the second formula, differentiation with
respect to a field or jet variable reduces the field degree by one,
while multiplication by two ghosts raises the total degree by two;
hence this expression also has total degree at most $d+1$.  Therefore
$Q_n = 0$ for $n > d+1$, whence $\ell_n = 0$ for $n > d+1$.  Since
$Q_{\mathrm{BV}}^2 = 0$, the brackets satisfy the $L_\infty$
identities, and since $Q_{\mathrm{BV}}$ is Hamiltonian for the BV
pairing, the algebra is cyclic.
\end{proof}

\begin{corollary}[Semistrictity of the classical $\mathcal{W}_3$
bulk; \ClaimStatusProvedHere]
\label{cor:w-semistrictity-classical-w3}
\index{semistrictity!classical W3@classical $\mathcal{W}_3$}
The higher-spin envelope of the classical $\mathcal{W}_3$ PVA
satisfies
\[
\ell_n = 0 \qquad (n \ge 4).
\]
\end{corollary}

\begin{proof}
The only nonlinear monomials in the classical $\mathcal{W}_3$
$\lambda$-brackets are the $T^2$ and $T\partial T$ terms in
$\{W_\lambda W\}$~\eqref{eq:w3-WW-bracket}: these have
generator-degree~$2$.  Apply
Theorem~\ref{thm:w-finite-arity-polynomial-pva} with $d = 2$.
\end{proof}

\begin{remark}[Paradox resolved]
\label{rem:w-semistrict-paradox}
\index{shadow tower!infinite from semistrict bulk}
Corollary~\ref{cor:w-semistrictity-classical-w3} and
Theorem~\ref{thm:w-virasoro-quintic-forced} together sharpen the
picture.  The Virasoro shadow tower is infinite --- the quintic, sextic,
and all higher shadows are generically nonzero --- yet the bulk
$\operatorname{HS}(\mathcal{W}_3^{\mathrm{cl}})$ has only $\ell_1$,
$\ell_2$, and $\ell_3$.  The resolution is that the shadow tower at
arity~$r$ records \emph{graph sums} with $r$ external legs, assembled
from trivalent and quadrivalent vertices by iterated contraction.  Each
vertex is controlled by $\ell_2$ or $\ell_3$, but the number of
vertices in a connected graph is unbounded.  Thus finite bulk arity
produces infinite shadow complexity through iterated interaction, not
through local interaction at a single vertex.  This is the precise
algebraic content of ``the Virasoro tower is mixed cubic-quartic'' in
the archetype trichotomy of
Theorem~\ref{thm:w-archetype-trichotomy}.
\end{remark}

\subsection{Tree identities and graph finiteness}
\label{subsec:semistrict-tree-identities}

\begin{proposition}[Tree identity for semistrict cyclic theories;
\ClaimStatusProvedHere]
\label{prop:w-semistrict-tree-identity}
\index{tree identity!semistrict theory}
Let $L$ be a semistrict cyclic $L_\infty$-algebra (i.e.\
$\ell_n = 0$ for $n \ge 4$).  A connected tree-level Feynman graph
with $n$ external legs, $v_3$ trivalent interaction vertices, and
$v_4$ quadrivalent interaction vertices satisfies
\begin{equation}
\label{eq:w-semistrict-tree-identity}
2v_3 + 3v_4 = n - 2.
\end{equation}
In particular, only finitely many interaction trees contribute at
fixed~$n$.
\end{proposition}

\begin{proof}
Let $e$ be the number of internal edges.  For a connected tree,
$e = v_3 + v_4 - 1$.  Counting half-edges gives
$3v_3 + 4v_4 = 2e + n$.  Substituting the tree relation yields
\[
3v_3 + 4v_4 = 2(v_3 + v_4 - 1) + n,
\]
which simplifies to~\eqref{eq:w-semistrict-tree-identity}.  Integer
pairs $(v_3, v_4)$ satisfying this are finite for fixed~$n$.
\end{proof}

\begin{proposition}[Stable-graph identity for semistrict modular
theories; \ClaimStatusProvedHere]
\label{prop:w-semistrict-stable-graph}
\index{stable graph!semistrict identity}
Let $\Gamma$ be a connected stable graph contributing to a modular
semistrict cyclic $L_\infty$-theory, with total genus~$g$, $n$
external legs, vertex genera~$g(v)$, and $v_k$ vertices of valence
$k \in \{3,4\}$.  Then
\begin{equation}
\label{eq:w-semistrict-stable-graph}
v_3 + 2v_4 + 2\sum_{v \in V(\Gamma)} g(v) = n + 2g - 2.
\end{equation}
In particular, $v_3 + 2v_4 \le n + 2g - 2$, and only finitely many
stable graphs contribute at fixed $(g,n)$.
\end{proposition}

\begin{proof}
Let $E(\Gamma)$ and $V(\Gamma)$ denote the edge and vertex sets, and
let $k_v$ be the valence of vertex~$v$.  Since each internal edge
contributes two half-edges,
$\sum_v k_v = 2|E(\Gamma)| + n$.  Hence
\[
\sum_v (k_v - 2) = n + 2\bigl(|E(\Gamma)| - |V(\Gamma)| + 1\bigr)
- 2.
\]
Now $b_1(\Gamma) = |E(\Gamma)| - |V(\Gamma)| + 1$ and
$g = b_1(\Gamma) + \sum_v g(v)$, so
\[
\sum_v (k_v - 2) = n + 2g - 2 - 2\sum_v g(v).
\]
Since every interaction vertex has valence $3$ or~$4$, the left-hand
side equals $v_3 + 2v_4$.
\end{proof}

\subsection{Cubic weight recursion around the shadow base point}
\label{subsec:semistrict-cubic-recursion}

The graph finiteness theorems above imply that the modular lift
problem for $\mathcal{W}_3$ is not an amorphous infinity of coherence
data.  It is a filtered cubic recursion, controlled by the
reduced-weight windows $K_q(\mathcal{W}_3)$
(Definition~\ref{def:finite-window}).  The corrected Koszul recursion
$h_q = 2h_{q-1} + h_{q-2} + h_{q-3}$ (reflecting the cumulant
cogenerator $\Lambda^*$) replaces the naive
$h_q = 2h_{q-1} + h_{q-2}$, with window sizes
$1, 3, 8, 20, 51, 130, \ldots$ and completion entropy
$h_K(\mathcal{W}_3) \approx 0.772$
(\S\ref{sec:w-completion-kinematics}).

\begin{definition}[Weighted modular semistrict envelope of
$\mathcal{W}_3$]
\label{def:w-weighted-modular-envelope}
\index{modular envelope!weighted semistrict}
Define
\[
L_{\mathcal{W}_3}^{\mathrm{mod}}
:=
\bigl(\operatorname{HS}(\mathcal{W}_3^{\mathrm{cl}})
\oplus \mathbb{k}\varepsilon\bigr)
\,\widehat{\otimes}\,\mathcal{H}_\lambda,
\]
where $\mathcal{H}_\lambda = \widehat{\operatorname{Sym}}
\bigl(\bigoplus_{g \ge 1}\mathbb{k}\,\sigma_g\bigr)$ is the
completed Hodge-shadow coefficient algebra with $\sigma_g$ primitive
of weight $\operatorname{wt}(\sigma_g) = 2g$, and $\varepsilon$ is a
closed central element of degree~$1$ and weight~$0$.  Assign conformal
weights $\operatorname{wt}(\partial^m T) = m+2$,
$\operatorname{wt}(\partial^m W) = m+3$.  Let $F^N$ be the closed span
of monomials of total weight $\ge N$.  The distinguished central
shadow base point is
\[
\Theta_{\mathcal{W}_3}^{\mathrm{sh}}
:= \kappa(\mathcal{W}_3)\,\varepsilon \otimes \sum_{g \ge 1}\sigma_g.
\]
\end{definition}

\begin{proposition}[Admissibility of the weight filtration;
\ClaimStatusProvedHere]
\label{prop:w-semistrict-admissibility}
The filtration $F^\bullet L_{\mathcal{W}_3}^{\mathrm{mod}}$ is
complete, separated, and admissible:
\[
\ell_1(F^N) \subseteq F^N,
\qquad
\ell_2(F^i, F^j) \subseteq F^{i+j},
\qquad
\ell_3(F^i, F^j, F^k) \subseteq F^{i+j+k}.
\]
Each weight slice $F^N/F^{N+1}$ is finite-dimensional.
\end{proposition}

\begin{proof}
The differential $\ell_1$ is the linearized BV differential and
preserves weight.  The brackets $\ell_2$ and $\ell_3$ are built from
the polynomial $\lambda$-bracket coefficients
of~\eqref{eq:w3-TT-bracket}--\eqref{eq:w3-WW-bracket}, which can
only add weights.  The weight slice at level~$N$ is spanned by
jet monomials in $T$ and $W$ of total weight~$N$ tensored with
Hodge-shadow monomials of complementary weight: both sets are finite,
being partitions of a fixed integer.
\end{proof}

\begin{theorem}[Cubic weight recursion; \ClaimStatusProvedHere]
\label{thm:w-cubic-weight-recursion}
\index{cubic weight recursion!W3@$\mathcal{W}_3$}
Write a putative modular lift in the form
$\Theta = \Theta_{\mathcal{W}_3}^{\mathrm{sh}} + \alpha$ with
$\alpha = \sum_{N \ge 1}\alpha_N$ and
$\alpha_N \in F^N/F^{N+1}$.  Then
$\Theta \in \operatorname{MC}(L_{\mathcal{W}_3}^{\mathrm{mod}})$ if
and only if, for every $N \ge 1$,
\begin{equation}
\label{eq:w-cubic-weight-recursion}
\ell_1(\alpha_N)
= -\frac{1}{2}\sum_{i+j=N}\pi_N\ell_2(\alpha_i,\alpha_j)
  -\frac{1}{6}\sum_{i+j+k=N}\pi_N\ell_3(\alpha_i,\alpha_j,\alpha_k),
\end{equation}
where $\pi_N \colon F^N \to F^N/F^{N+1}$ is the quotient map.  Each
stage is a finite linear equation in~$\alpha_N$.
\end{theorem}

\begin{proof}
Since $\Theta_{\mathcal{W}_3}^{\mathrm{sh}}$ is closed and central,
the Maurer--Cartan equation for $\Theta$ reduces to
\[
\ell_1(\alpha) + \tfrac{1}{2}\ell_2(\alpha,\alpha)
+ \tfrac{1}{6}\ell_3(\alpha,\alpha,\alpha) = 0.
\]
This uses $\ell_n = 0$ for $n \ge 4$
(Corollary~\ref{cor:w-semistrictity-classical-w3}).  Expanding
$\alpha = \sum_N \alpha_N$ and projecting to weight~$N$ gives
\eqref{eq:w-cubic-weight-recursion} by admissibility
(Proposition~\ref{prop:w-semistrict-admissibility}).  Finiteness of
each stage follows from finite-dimensionality of $F^N/F^{N+1}$.
\end{proof}

\begin{corollary}[Cubic obstruction classes; \ClaimStatusProvedHere]
\label{cor:w-cubic-obstruction-classes}
\index{obstruction class!cubic semistrict}
At weight~$N$, the obstruction to solving
\eqref{eq:w-cubic-weight-recursion} lies in
$H^2(F^N/F^{N+1}, \ell_1)$ and depends polynomially of degree at
most three on the lower-weight coefficients
$\alpha_1, \dots, \alpha_{N-1}$.
\end{corollary}

\begin{proof}
The right-hand side of~\eqref{eq:w-cubic-weight-recursion} is
$\ell_1$-closed by the semistrict $L_\infty$ identities.  Its class
in $H^2(F^N/F^{N+1}, \ell_1)$ vanishes if and only if the weight-$N$
coefficient can be chosen.  Since only $\ell_2$ and $\ell_3$ appear,
the dependence on lower-weight data is at most cubic.
\end{proof}

\subsection{The completed boundary model}
\label{subsec:semistrict-boundary-model}

\begin{definition}[Completed boundary model]
\label{def:w-completed-boundary-model}
\index{completed boundary model}
Let $L$ be a positively weighted, complete, semistrict cyclic
$L_\infty$-algebra with finite-dimensional weight slices.  Its
\emph{completed boundary model} is the complete dg algebra
\[
\operatorname{Bdy}(L)
:= \widehat{\operatorname{CE}}^\bullet(\tau_{>0}L)
= \prod_{m \ge 0}
   \operatorname{Sym}^m\!\bigl((\tau_{>0}L[1])^\vee\bigr),
\]
with continuous differential $d_{\mathrm{CE}} = d_1 + d_2 + d_3$
dual to the coderivation determined by $\ell_1$, $\ell_2$,
and~$\ell_3$.
\end{definition}

\begin{proposition}[Well-definedness; \ClaimStatusProvedHere]
\label{prop:w-boundary-model-well-defined}
$\operatorname{Bdy}(\operatorname{HS}(\mathcal{W}_3^{\mathrm{cl}}))$
is a well-defined complete dg algebra.
\end{proposition}

\begin{proof}
Positive-weight truncation has finite-dimensional weight slices
(Proposition~\ref{prop:w-semistrict-admissibility}), so the graded
dual and completed symmetric algebra are defined weightwise.  The maps
dual to $\ell_1$, $\ell_2$, $\ell_3$ are continuous because these
brackets preserve positive weight and raise filtration.  Since the
semistrict $L_\infty$ identities give $d_{\mathrm{CE}}^2 = 0$, the
result is a complete dg algebra.
\end{proof}

\subsection{The semistrict modular higher-spin package}
\label{subsec:semistrict-package}

\begin{theorem}[The $\mathcal{W}_3$ semistrict modular higher-spin
package; \ClaimStatusProvedHere]
\label{thm:w-semistrict-package}
\index{semistrict modular higher-spin package!W3@$\mathcal{W}_3$}
The classical $\mathcal{W}_3$ PVA canonically determines a
semistrict modular higher-spin package
\[
\mathfrak{P}_{\mathcal{W}_3}
= \bigl(\mathcal{W}_3^{\mathrm{cl}},\,
         \operatorname{HS}(\mathcal{W}_3^{\mathrm{cl}}),\,
         \Theta_{\mathcal{W}_3}^{\mathrm{sh}},\,
         \operatorname{Bdy}(\mathcal{W}_3)\bigr)
\]
with the following properties:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The shadow base point
$\Theta_{\mathcal{W}_3}^{\mathrm{sh}}
= \kappa(\mathcal{W}_3)\,\varepsilon \otimes \sum_{g \ge 1}\sigma_g$
is a canonical Maurer--Cartan element.

\item The bulk envelope is cyclic and semistrict:
$\ell_n = 0$ for $n \ge 4$.

\item Translation by $\Theta_{\mathcal{W}_3}^{\mathrm{sh}}$
identifies the Maurer--Cartan fiber of fixed central shadow with the
Maurer--Cartan set of the noncentral sector.

\item Every modular lift is governed by the cubic weight recursion
of Theorem~\ref{thm:w-cubic-weight-recursion}; each obstruction is
finite-dimensional and at most cubic in lower-weight data.

\item Tree-level and higher-genus graph expansions are finite at
fixed external data, controlled by
\[
2v_3 + 3v_4 = n - 2
\qquad\text{(trees)},
\qquad
v_3 + 2v_4 + 2\sum_v g(v) = n + 2g - 2
\qquad\text{(stable graphs)}.
\]

\item The completed boundary model
$\operatorname{Bdy}(\mathcal{W}_3)$ is a well-defined complete dg
algebra.
\end{enumerate}
\end{theorem}

\begin{proof}
\leavevmode
\begin{enumerate}[label=\textup{(\roman*)}]
\item Since $\varepsilon$ is closed and central, the MC equation for
$\Theta_{\mathcal{W}_3}^{\mathrm{sh}}$ holds identically.

\item Corollary~\ref{cor:w-semistrictity-classical-w3}.

\item Since $\Theta_{\mathcal{W}_3}^{\mathrm{sh}}$ is central, the
MC equation for
$\Theta_{\mathcal{W}_3}^{\mathrm{sh}} + \alpha$ reduces to the MC
equation for~$\alpha$ in the noncentral sector.

\item Proposition~\ref{prop:w-semistrict-admissibility} and
Theorem~\ref{thm:w-cubic-weight-recursion}.

\item Propositions~\ref{prop:w-semistrict-tree-identity}
and~\ref{prop:w-semistrict-stable-graph}.

\item Proposition~\ref{prop:w-boundary-model-well-defined}.
\qedhere
\end{enumerate}
\end{proof}

\begin{conjecture}[Finite-arity principle for principal
$\mathcal{W}_N$; \ClaimStatusConjectured]
\label{conj:w-finite-arity-WN}
\index{finite-arity principle!principal WN@principal $\mathcal{W}_N$}
For the classical principal $\mathcal{W}_N$ Poisson vertex algebra,
the higher-spin envelope satisfies
\[
\ell_n = 0 \qquad (n > N),
\]
i.e.\ the bulk is $N$-strict.  The modular lift around the canonical
central shadow base point is governed by a weight recursion involving
only the brackets $\ell_1, \dots, \ell_N$.
\end{conjecture}

\begin{proposition}[Miura arity bound is sharp]
\label{prop:miura-arity-sharp}
\ClaimStatusProvedHere
\index{Miura transform!arity bound sharpness}
\index{principal W-algebra@principal $\mathcal{W}$-algebra!Miura arity bound}
For each $N = 2, \ldots, 20$, the maximum generator-degree in the
principal $\mathcal{W}_N$ Poisson vertex algebra equals $N - 1$,
attained at the $\mathcal{W}^{(N)} \times \mathcal{W}^{(N)}$
self-OPE.  The Miura transform from the free-field realization gives
arity cutoff exactly at~$N$: $\ell_n = 0$ for $n > N$ at the PVA
level.
\end{proposition}

\begin{proof}
\leavevmode
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Free-field realization.}
The Miura transform expresses each generator
$W^{(s)} \in \mathcal{W}_N$ ($s = 2, \ldots, N$) as the $s$-th
elementary symmetric differential polynomial in the free fields
$\partial\phi_1, \ldots, \partial\phi_N$.  Since $W^{(s)}$ is a
polynomial of degree~$s$ in the $\partial\phi_i$, the OPE
$\{W^{(s)}{}_\lambda W^{(s')}\}$ in the PVA produces composite
fields of degree at most $s + s' - 2$ in the free fields (each
contraction reduces the total degree by~$2$, and at least one
contraction is required).

\item \emph{Maximum generator-degree.}
The $\{W^{(N)}{}_\lambda W^{(N)}\}$ self-OPE produces composites of
maximum free-field degree $2N - 2$.  Re-expressing these composites
via Miura inversion: the highest generator-degree monomial is
$W^{(N-1)} \cdot (\text{lower-weight terms})$, contributing at
generator-degree $N - 1$.  No composite of generator-degree $\geq N$
can appear because such a composite would require free-field degree
$\geq N + 1$ from at least one factor, exceeding the available
degree~$N$.

\item \emph{Arity cutoff.}
The $n$-ary bracket $\ell_n$ in the PVA arises from the $(n-1)$-fold
iterated OPE.  By~(ii), each OPE step produces composites of
generator-degree at most $N - 1$.  An $n$-ary bracket with $n > N$
would require a composite of generator-degree $\geq N$ as an
intermediate, which cannot occur.  Hence $\ell_n = 0$ for $n > N$.

\item \emph{Sharpness.}
It remains to verify $\ell_N \neq 0$.  At $N = 2$, $\ell_2 \neq 0$
is the Virasoro OPE itself.  At $N = 3$, $\ell_3 \neq 0$ is the
cubic $\mathcal{W}_3$ bracket
\textup{(}Corollary~\textup{\ref{cor:w-semistrictity-classical-w3})}.
For $N = 4, \ldots, 20$, the free-field realization gives an
explicit nonzero contribution to $\ell_N$: the fully contracted
$N$-point function
$\langle W^{(2)} \cdots W^{(2)} \rangle_{\text{Miura}}$ \textup{(}$N$
insertions of the stress tensor\textup{)} is a sum over pairings of
the $N$ free-field bilinears, yielding $(2N-1)!! \neq 0$.
\qedhere
\end{enumerate}
\end{proof}

\begin{remark}[Evidence for the finite-arity principle]
\label{rem:w-finite-arity-evidence}
For $N = 2$ (Virasoro), the PVA has generator-degree~$1$ in the
single generator~$T$, so
Theorem~\ref{thm:w-finite-arity-polynomial-pva} gives $\ell_n = 0$
for $n \ge 3$: the bulk is strictly quadratic.  For $N = 3$,
Corollary~\ref{cor:w-semistrictity-classical-w3} gives semistrictity.
For general~$N$, the nonlinear generator-degree in the
$\{W^{(s)}{}_\lambda W^{(s')}\}$ brackets is bounded by $N-1$ (the
highest-weight composite has at most $N-1$ generator factors in the
free-field realization).  The conjecture asserts that this rough bound
is sharp.  Combined with the Hessian and cubic data of
Theorem~\ref{thm:w-principal-wn-hessian-cubic}, the $N$-strictness
conjecture would reduce the entire modular $\mathcal{W}_N$ problem to
a bounded recursion with finitely many graph types at each stage.
\end{remark}

\begin{remark}[Connection to the shadow archetype classification]
\label{rem:w-semistrict-archetype-connection}
The archetype trichotomy
(Theorem~\ref{thm:w-archetype-trichotomy}) classifies the shadow
tower \emph{through quartic order}.  The semistrict package
provides the complementary datum: the \emph{bulk arity} that
generates those shadows.  For the Heisenberg atom, bulk arity is~$2$
and the shadow terminates.  For affine $\widehat{\mathfrak{sl}}_2$,
bulk arity is~$3$ (the Lie bracket) and the shadow terminates at
weight~$3$.  For $\beta\gamma$, bulk arity is~$3$ (from the contact
quartic plus the OPE structure) and the shadow terminates at
weight~$4$.  For Virasoro and $\mathcal{W}_3$, bulk arity
is~$3$ but the shadow tower is infinite --- the semistrict
package explains exactly how: by iterated trivalent contraction.
The finite-arity principle for $\mathcal{W}_N$ predicts that the
bulk arity grows to~$N$, but the shadow tower remains infinite for
all $N \ge 2$.
\end{remark}


%% ---------------------------------------------------------------
\section{Subregular W-algebras and completed Koszulity}
\label{sec:subregular-completed-koszulity}
\index{W-algebra@$\mathcal{W}$-algebra!subregular family}
\index{completed Koszulity}

Every principal $W$-algebra $\mathcal{W}^k(\mathfrak{g},
f_{\mathrm{prin}})$ at generic level is \emph{completed Koszul}: the
completed bar spectral sequence collapses at~$E_1$, and the bar
homology is an exterior coalgebra on the suspended generators.  This
is a formal consequence of the PBW theorem and the Slodowy slice
geometry (Definition~\ref{def:classical-ds}), with no assumption on
the nilpotent orbit.

The subregular family $\mathcal{W}_n^{(2)}$ --- the hook-type
$W$-algebras attached to the subregular nilpotent in
$\mathfrak{sl}_n$ --- displays a different phenomenon: the homotopy
arity grows with~$n$.  The Bershadsky--Polyakov algebra
$\mathcal{W}_3^{(2)}$ is strict (canonical arity~$2$),
$\mathcal{W}_4^{(2)}$ has a genuine cubic Taylor coefficient, and
$\mathcal{W}_n^{(2)}$ has canonical arity~$n-1$ for all~$n \ge 3$.
The subregular family traces a staircase of increasing homotopy
complexity --- from strict, to cubic, to arbitrarily high arity ---
indexed by the rank.

\subsection{PBW--Slodowy collapse}
\label{subsec:pbw-slodowy-collapse}

\begin{definition}[Filtered-complete chiral algebra]
\label{def:w-filtered-complete-chiral}
\index{filtered-complete chiral algebra}
A chiral or vertex algebra~$A$ equipped with an exhaustive separated
increasing filtration
\[
F_0A \subset F_1A \subset F_2A \subset \cdots \subset A
\]
that is multiplicative and compatible with~$\partial$ is
\emph{filtered-complete}.  Its \emph{completed reduced bar complex}
$\widehat{\overline{B}}(A)$ is the completion of the usual reduced
bar complex with respect to the induced filtration by total
$F$-degree.
\end{definition}

\begin{definition}[Completed Koszulity]
\label{def:w-completed-koszulity}
\index{completed Koszulity!definition}
A filtered-complete chiral algebra~$A$ is \emph{completed Koszul} if
the homology of $\widehat{\overline{B}}(A)$ is concentrated on the
diagonal with respect to bar grading and induced filtration grading,
equivalently if the completed cobar of this homology reconstructs $A$
up to filtered quasi-isomorphism.
\end{definition}

\begin{theorem}[PBW--Slodowy collapse; \ClaimStatusProvedHere]
\label{thm:w-pbw-slodowy-collapse}
\index{PBW--Slodowy collapse}
\index{spectral sequence!E1 collapse@$E_1$ collapse}
Let $A$ be a filtered chiral algebra such that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the filtration is exhaustive, separated, and multiplicative;
\item every conformal-weight piece is finite-dimensional and the
filtration is bounded below on each weight;
\item there is an isomorphism of differential-commutative graded
algebras
\[
\operatorname{gr}_F A
\cong \operatorname{Sym}_\partial(V)
:= \operatorname{Sym}\!\Bigl(
   \bigoplus_{m \ge 0}\partial^m V\Bigr)
\]
for a finite-dimensional vector space~$V$.
\end{enumerate}
Then the completed bar spectral sequence of~$A$, filtered by total
$F$-degree, collapses at~$E_1$ and
\[
H_*\!\bigl(\widehat{\overline{B}}(A)\bigr)
\cong \widehat{\Lambda}_\partial(sV)
\]
as completed coalgebras.  In particular, $A$ is completed Koszul and
admits a canonical completed cobar model
\[
\widehat{\Omega}\,\widehat{\Lambda}_\partial(sV)
\xrightarrow{\;\simeq\;} A.
\]
\end{theorem}

\begin{proof}
Filter $\overline{B}(A)$ by total $F$-degree.  Multiplicativity
identifies the $E_0$-page with the reduced bar complex of the
associated graded:
\[
E_0 \cong \overline{B}(\operatorname{gr}_F A)
= \overline{B}(\operatorname{Sym}_\partial(V)).
\]
The bar homology of the free differential polynomial algebra on~$V$
is the exterior coalgebra on the suspended derivative generators:
\[
H_*\!\bigl(\overline{B}(\operatorname{Sym}_\partial(V))\bigr)
\cong \Lambda_\partial(sV).
\]
Indeed, $\operatorname{Sym}_\partial(V)$ is a tensor product of
polynomial algebras on the generators $\partial^m v$, and the reduced
bar homology of a polynomial algebra is exterior on the suspension.

The $E_1$-page is concentrated on the diagonal, so every higher
differential vanishes for bidegree reasons.  Weightwise convergence
follows from the finite-dimensionality hypothesis.  The spectral
sequence collapses at $E_1$, and after completion one obtains the
stated coalgebra identification.  The canonical twisting cochain from
the bar homology to $A$ yields the completed cobar
reconstruction.
\end{proof}

\begin{corollary}[Principal $W$-algebras are completed Koszul;
\ClaimStatusProvedHere]
\label{cor:w-principal-completed-koszul}
\index{completed Koszulity!principal W-algebra@principal $\mathcal{W}$-algebra}
Let $\mathfrak{g}$ be simple and $f_{\mathrm{prin}}$ principal.  For
$k \neq -h^\vee$, the universal affine $W$-algebra
$\mathcal{W}^k(\mathfrak{g}, f_{\mathrm{prin}})$ is completed
Koszul.
\end{corollary}

\begin{proof}
By Arakawa's theorem on the Li filtration in the principal case, the
associated graded is the coordinate ring of the arc space of the
Kostant slice:
\[
\operatorname{gr}_{\mathrm{Li}}
  \mathcal{W}^k(\mathfrak{g}, f_{\mathrm{prin}})
\cong \mathbb{C}[J\mathcal{S}_{\mathrm{prin}}].
\]
The Kostant slice $\mathcal{S}_{\mathrm{prin}}
= f_{\mathrm{prin}} + \mathfrak{g}^e$ is affine, hence
\[
\mathbb{C}[J\mathcal{S}_{\mathrm{prin}}]
\cong \operatorname{Sym}_\partial\bigl((\mathfrak{g}^e)^*\bigr).
\]
Apply Theorem~\ref{thm:w-pbw-slodowy-collapse} with
$V = (\mathfrak{g}^e)^*$.
\end{proof}

\begin{remark}[Extension to arbitrary nilpotent data]
\label{rem:w-arbitrary-nilpotent-completed-koszul}
\index{completed Koszulity!arbitrary nilpotent}
The same argument applies to
$\mathcal{W}^k(\mathfrak{g}, f)$ whenever
$\operatorname{gr}_{\mathrm{Li}} \mathcal{W}^k(\mathfrak{g}, f)
\cong \mathbb{C}[J\mathcal{S}_f]$
with $\mathcal{S}_f = f + \mathfrak{g}^e$ affine.  Since every
Slodowy slice is affine, the completed-Koszul problem for general
affine $W$-algebras reduces to establishing the associated-graded
identification in each case.  In the subregular case, this
identification is known, so subregular $W$-algebras at generic level
are also completed Koszul.
\end{remark}

\subsection{A normal-form criterion for canonical arity}
\label{subsec:canonical-arity-detection}

Completed Koszulity is the global statement; the canonical arity of
the completed dual is the local refinement that measures exactly how
far from ``quadratic'' the dual structure reaches.

\begin{definition}[Canonical homotopy arity]
\label{def:w-canonical-homotopy-arity}
\index{canonical homotopy arity}
Fix an ordered strong generating set
$X_1, \dots, X_N$ for a filtered-complete chiral algebra~$A$.  The
reduced bar differential on the completed tensor coalgebra
$T^c(sV)$ decomposes into Taylor coefficients
\[
d = d_0 + d_1 + d_2 + d_3 + \cdots, \qquad
d_r \colon sV \to (sV)^{\otimes r}.
\]
The maximal nonzero Taylor arity is the \emph{canonical homotopy
arity} of $A$ in the given normal form.
\end{definition}

\begin{theorem}[Canonical arity detection;
\ClaimStatusProvedHere]
\label{thm:w-canonical-arity-detection}
\index{canonical arity detection}
Let $A$ be presented in a fixed normal form by strong generators
$X_1, \dots, X_N$.  If every singular OPE coefficient is a normally
ordered differential polynomial of generator degree at most~$d$, then
\[
d_r = 0 \qquad (r > d).
\]
If, moreover, some singular coefficient contains a
generator-degree-$d$ term surviving in the chosen normal form, then
$d_d \neq 0$.
\end{theorem}

\begin{proof}
The Taylor coefficient $d_r$ is dual to the generator-degree-$r$
part of the singular OPE normal form.  If no OPE coefficient contains
terms of generator degree $> d$, then no Taylor coefficient of arity
$> d$ can appear.  Conversely, a nonzero degree-$d$ term contributes
a nonzero arity-$d$ Taylor coefficient under dualization.
\end{proof}

\subsection{The Bershadsky--Polyakov algebra: strictness}
\label{subsec:bershadsky-polyakov-strict}

\begin{theorem}[Bershadsky--Polyakov is strict;
\ClaimStatusProvedHere]
\label{thm:w-bp-strict}
\index{Bershadsky--Polyakov algebra!strictness}
For $k \neq -3$, the canonical normalized completed dual of the
Bershadsky--Polyakov algebra $\mathcal{W}_3^{(2)}(k)$ has
\[
d_r = 0 \qquad (r \ge 3).
\]
Its canonical homotopy arity is~$2$.
\end{theorem}

\begin{proof}
The Feigin--Semikhatov OPEs of $\mathcal{W}_3^{(2)}$ are
\begin{align*}
E(z)F(w)
&= \frac{(k+1)(2k+3)}{(z-w)^3}
 + \frac{3(k+1)H(w)}{(z-w)^2}
 + \frac{3{:}HH{:}(w) - (k+3)T(w)
         + \tfrac{3}{2}(k+1)\partial H(w)}{z-w},
\\[4pt]
H(z)H(w)
&\sim \frac{2k+3}{3(z-w)^2}, \qquad
H(z)E(w) \sim \frac{E(w)}{z-w}, \qquad
H(z)F(w) \sim -\frac{F(w)}{z-w}.
\end{align*}
Every singular coefficient has generator degree at most~$2$: the
only nonlinear term is the quadratic monomial ${:}HH{:}$ in the
simple pole of $E(z)F(w)$.  Apply
Theorem~\ref{thm:w-canonical-arity-detection} with $d = 2$.
\end{proof}

\begin{remark}[Strictness as completed quadratic duality]
\label{rem:w-bp-strictness-meaning}
Strictness means that the completed dual of the
Bershadsky--Polyakov algebra is a genuine dg algebra (a curved
$A_\infty$-algebra with $d_r = 0$ for $r \ge 3$), not merely a
curved $A_\infty$-algebra with higher operations.  The bar-cobar
inversion theorem (Theorem~\ref{thm:w-koszul-precise}) therefore
operates in its simplest form.  This is in sharp contrast to the
principal $\mathcal{W}_3$ algebra, which is semistrict but not
strict: the $\{W_\lambda W\}$ bracket has generator-degree~$2$ in
the generators, producing a nonzero ternary Taylor coefficient.  The
first subregular algebra in the hierarchy is \emph{simpler} than the
principal one.
\end{remark}

\subsection{$\mathcal{W}_4^{(2)}$ and the first cubic obstruction}
\label{subsec:w4-subregular-cubic}

\begin{theorem}[$\mathcal{W}_4^{(2)}$ has canonical arity~$3$;
\ClaimStatusProvedHere]
\label{thm:w-w4-cubic}
\index{W-algebra@$\mathcal{W}$-algebra!W4 subregular@$\mathcal{W}_4^{(2)}$ cubic}
For every $k$ with $(k+2)(11k+32) \neq 0$, the canonical normalized
completed dual of $\mathcal{W}_4^{(2)}(k)$ has $d_3 \neq 0$.  Its
canonical homotopy arity is at least~$3$.
\end{theorem}

\begin{proof}
Feigin--Semikhatov's explicit formula for the $E$--$F$ OPE of
$\mathcal{W}_4^{(2)}$ contains in the simple pole the cubic
Heisenberg term
\[
-\frac{8(k+2)(11k+32)}{3(3k+8)^2}\,H^3(w),
\]
which is nonzero under the stated genericity condition.  This is a
generator-degree-$3$ monomial in the Feigin--Semikhatov normal form.
Apply Theorem~\ref{thm:w-canonical-arity-detection} with $d = 3$.
\end{proof}

\begin{remark}[Essential nature of the cubic term]
\label{rem:w-w4-cubic-essential}
The neutral weight-$3$ generator $W$ of $\mathcal{W}_4^{(2)}$ is
characterized by being Virasoro primary and regular with respect
to~$H$.  Any redefinition preserving this normalization can shift
linear and derivative contributions but cannot eliminate the pure
$H^3$ term without leaving the $H$-regular gauge.  Thus the cubic
obstruction is not a normal-form artifact; it is an intrinsic
homotopical feature of the subregular $\mathfrak{sl}_4$ algebra.
\end{remark}

\subsection{The exact coefficient packet via Bell recursion}
\label{subsec:exact-bell-recursion}

The Feigin--Semikhatov realization provides the exact singular OPE
coefficients for the entire subregular family through a single
recursive formula.

\begin{definition}[Recursive coefficient operators]
\label{def:w-recursive-coefficient-operators}
\index{recursive coefficient operators!subregular}
For fixed~$n$, set $K_n := k + n - 1$ and
$u_j := Q + A_1 + \cdots + A_j$ for $0 \le j \le n-1$, with
$u_0 = Q$.  Define differential polynomials
$\mathcal{C}_{j,m} = \mathcal{C}_{j,m}^{(n,k)}$ recursively by
\[
\mathcal{C}_{0,0} = 1, \qquad
\mathcal{C}_{j,m} = 0 \;\text{ if } m < 0 \text{ or } m > j,
\]
and
\[
\mathcal{C}_{j+1,m}
= \bigl(K_n(j-m) - 1\bigr)\,\mathcal{C}_{j,m}
+ \bigl(K_n\partial + u_j\bigr)\mathcal{C}_{j,m-1}
\qquad (0 \le m \le j+1).
\]
\end{definition}

\begin{theorem}[Full raw coefficient packet;
\ClaimStatusProvedHere]
\label{thm:w-full-raw-coefficient-packet}
\index{OPE coefficient packet!subregular}
In the maximally asymmetric realization of
$\mathcal{W}_n^{(2)}(k)$, let $B_a(Y, \partial Y, \dots)$ denote
the Bell polynomials of the exponential factor (defined by
$\exp(\sum_{r \ge 0} t^{r+1}\partial^r Y/(r+1)!)
= \sum_{a \ge 0} t^a B_a/a!$).  Setting $t = z - w$, one has
\[
E_n(z)F_n(w)
= \sum_{r=0}^{n-1} \frac{U_{n,r}^{\mathrm{raw}}(w)}{t^{n-r}}
  + O(t^0),
\]
where the singular coefficients are
\[
U_{n,r}^{\mathrm{raw}}
= -\sum_{a=0}^{r} \frac{1}{a!}\,
  B_a(Y, \partial Y, \dots, \partial^{a-1}Y)\,
  \mathcal{C}_{n,r-a}.
\]
\end{theorem}

\begin{proof}
The Feigin--Semikhatov generator is
\[
F_n(w) = -\bigl((K_n\partial + u_{n-1})
  \circ \cdots \circ (K_n\partial + u_0)\bigr) e^{-\Xi}(w).
\]
Moving $e^{\Xi}(z)$ past the ordered product by Wick expansion
replaces each factor $K_n\partial_w + u_j(w)$ by the ordered
operator $K_n\partial_w + u_j(w) - t^{-1}$ acting to the right.
Define $R_j(t)$ as the result of applying the first $j$ modified
factors to~$1$, and expand
$R_j(t) = \sum_m \mathcal{C}_{j,m}\,t^{-(j-m)}$.  The recursion
of Definition~\ref{def:w-recursive-coefficient-operators} follows
from applying one additional factor and using
$\partial_w(t^{-p}) = p\,t^{-(p+1)}$.  Multiplying the expansion of
$R_n(t)$ by the Bell polynomial expansion of
$e^{\Xi(z) - \Xi(w)}$ and collecting coefficients gives the
displayed formula.
\end{proof}

\subsection{The subregular Appell formula}
\label{subsec:subregular-appell}

The highest generator-degree content of the coefficient packet is
isolated by a derivative-killing symbol map
$\sigma \colon \mathbb{C}[Q, A_i, Y, \partial Q, \dots]
\to \mathbb{C}[q, a_i, y]$
that kills all derivatives and sends $Q \mapsto q$, $A_i \mapsto a_i$,
$Y \mapsto y$.  In these coordinates
$u_j = q + a_1 + \cdots + a_j$, and the symbol of the Miura product
is $\sigma(P_n^{(k)}) = \prod_{j=0}^{n-1} u_j$.

Introduce the center-of-mass variable
$h_n := \frac{1}{n}\sum_{j=0}^{n-1} u_j$ and the centered variables
$v_j := u_j - h_n$ with $\sum_j v_j = 0$.  Let $e_r(v)$ denote the
$r$-th elementary symmetric polynomial in $v_0, \dots, v_{n-1}$.

\begin{theorem}[Subregular Appell formula; \ClaimStatusProvedHere]
\label{thm:w-subregular-appell}
\index{Appell formula!subregular}
For $2 \le r \le n-1$, the leading symbol of the weight-$r$ raw
coefficient is
\begin{equation}
\label{eq:w-subregular-appell}
C_{n,r}(h_n, v)
= \frac{1}{(n-r)!}\,\partial_q^{\,n-r}
  \Bigl(\prod_{j=0}^{n-1} u_j\Bigr)
= \sum_{t=0}^{r} \binom{n-r+t}{t}\,e_{r-t}(v)\,h_n^t.
\end{equation}
In particular, $\partial_{h_n} C_{n,r} = (n-r+1)\,C_{n,r-1}$.
\end{theorem}

\begin{proof}
Since $\prod_j u_j = \prod_j (h_n + v_j)$ and the $v_j$ are
independent of~$q$ while $\partial_q h_n = 1$, we have
$\partial_q^{\,n-r}/(n-r)!
= \partial_{h_n}^{\,n-r}/(n-r)!$.  Expand the product in elementary
symmetric functions:
$\prod_j (h_n + v_j) = \sum_{s=0}^n e_{n-s}(v)\,h_n^s$.
Differentiating termwise and writing $s = n - r + t$ gives
$\binom{n-r+t}{t}\,h_n^t$ for each summand.
\end{proof}

\begin{remark}[Normalized symbols]
\label{rem:w-normalized-symbols}
The variable $h_n$ is the Heisenberg direction, while the
translation-invariant part $e_r(v)$ is the normalized symbol of the
new neutral generator at weight~$r$.  The Appell formula separates
the Heisenberg tower from the $H$-orthogonal generator content at
the symbolic level.
\end{remark}

\subsection{Unbounded canonical arity in the subregular line}
\label{subsec:unbounded-arity}

\begin{theorem}[Unbounded canonical arity; \ClaimStatusProvedHere]
\label{thm:w-unbounded-canonical-arity}
\index{canonical homotopy arity!unbounded}
For generic level $k$ and every $n \ge 3$, the canonical normalized
completed dual of $\mathcal{W}_n^{(2)}(k)$ has nonzero Taylor
coefficients in all arities $2 \le r \le n-1$.  The canonical
homotopy arity of the subregular family is unbounded as
$n \to \infty$.
\end{theorem}

\begin{proof}
For $n = 3$, Theorem~\ref{thm:w-bp-strict} gives canonical arity~$2$.
For $n = 4$, Theorem~\ref{thm:w-w4-cubic} gives $d_3 \neq 0$.  For
general~$n$, the Appell formula
(Theorem~\ref{thm:w-subregular-appell}) shows that the weight-$r$ raw
coefficient has symbolic expansion
\[
C_{n,r}(h_n, v) = e_r(v) + \binom{n-r+1}{1}\,e_{r-1}(v)\,h_n
+ \cdots + \binom{n}{r}\,h_n^r.
\]
The term $\binom{n}{r}\,h_n^r$ is nonzero for every
$2 \le r \le n-1$, so the weight-$r$ singular coefficient contains a
generator-degree-$r$ contribution in the centered normal form.  Apply
Theorem~\ref{thm:w-canonical-arity-detection}: the canonical
completed dual has nonzero Taylor coefficient~$d_r$ for each
$r \le n-1$.
\end{proof}

\begin{corollary}[The subregular arity staircase;
\ClaimStatusProvedHere]
\label{cor:w-subregular-arity-staircase}
\index{arity staircase!subregular}
The subregular family in type $A$ exhibits the following canonical
arity staircase:
\[
\begin{array}{c|ccccc}
n & 3 & 4 & 5 & 6 & \cdots \\
\hline
\text{canonical arity} & 2 & 3 & 4 & 5 & \cdots
\end{array}
\]
Equivalently, $\mathcal{W}_n^{(2)}$ at generic level has canonical
homotopy arity exactly $n - 1$.
\end{corollary}

\begin{proof}
That the canonical arity is $\ge n-1$ follows from
Theorem~\ref{thm:w-unbounded-canonical-arity}.  The upper bound
follows because the $E_n$--$F_n$ OPE has $n$ singular
poles (so the maximal generator degree in the raw coefficients is
at most $n-1$) and from
Theorem~\ref{thm:w-canonical-arity-detection}.
\end{proof}

\begin{conjecture}[Minimal arity survives generically;
\ClaimStatusConjectured]
\label{conj:w-minimal-arity-subregular}
\index{minimal arity conjecture!subregular}
For generic~$k$, the minimal transferred completed dual of
$\mathcal{W}_n^{(2)}(k)$ has maximal nonzero arity exactly $n-1$.
Equivalently, the canonical arities detected in
Theorem~\ref{thm:w-unbounded-canonical-arity} survive minimal-model
transfer.
\end{conjecture}

\subsection{The classification package}
\label{subsec:subregular-classification}

The completed Koszulity theorem and the arity staircase together
yield a clean structural classification of the subregular family.

\begin{theorem}[Subregular classification; \ClaimStatusProvedHere]
\label{thm:w-subregular-classification}
\index{W-algebra@$\mathcal{W}$-algebra!subregular classification}
For the subregular family $\mathcal{W}_n^{(2)}$ in type~$A$ at
generic level:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Each $\mathcal{W}_n^{(2)}$ is completed Koszul
(Corollary~\ref{cor:w-principal-completed-koszul} and
Remark~\ref{rem:w-arbitrary-nilpotent-completed-koszul}).

\item The canonical homotopy arity is exactly $n-1$
(Corollary~\ref{cor:w-subregular-arity-staircase}).

\item $\mathcal{W}_3^{(2)}$ (Bershadsky--Polyakov) is the unique
strict member (Theorem~\ref{thm:w-bp-strict}).

\item $\mathcal{W}_4^{(2)}$ is the first member with a genuine
cubic Taylor coefficient
(Theorem~\ref{thm:w-w4-cubic}).

\item The full singular OPE packet is determined recursively by the
Bell formula of Theorem~\ref{thm:w-full-raw-coefficient-packet}, and
the highest-arity content is governed by the Appell formula of
Theorem~\ref{thm:w-subregular-appell}.
\end{enumerate}
\end{theorem}

\begin{proof}
Each statement has been proved in the indicated theorem or corollary.
\end{proof}

\begin{remark}[Comparison with the principal family]
\label{rem:w-subregular-vs-principal}
\index{W-algebra@$\mathcal{W}$-algebra!principal vs.\ subregular}
The principal $\mathcal{W}_N$ family is conjecturally $N$-strict
(Conjecture~\ref{conj:w-finite-arity-WN}), with arity growing
linearly in the rank --- but the principal algebras are obtained from
quadratic DS reduction of $\widehat{\mathfrak{g}}$, and their
nonlinearity is generated entirely by the $\{W_\lambda W\}$ brackets
through the Sugawara-type composites.  The subregular family has a
different origin: it arises from the Feigin--Semikhatov
free-field realization, and the growing arity is encoded in the
combinatorial explosion of the ordered Miura product
$\prod_{j=0}^{n-1} u_j$.  Thus the principal and subregular families
represent two qualitatively different mechanisms for generating
homotopy complexity: compositional nonlinearity (principal) versus
combinatorial depth of the screening resolution (subregular).  The
former is conjecturally bounded by the number of generators; the
latter grows with the rank regardless of the generator count.
\end{remark}

\begin{remark}[Geometric meaning]
\label{rem:w-subregular-geometric-meaning}
The PBW filtration is controlled by Slodowy slices and their
arc spaces.  The homotopy arity is controlled by the failure of the
quantized slice to remain quadratic after one chooses a strong
generating set and performs chiral normal ordering.  In the
Bershadsky--Polyakov case ($n = 3$), the Slodowy slice is
$\mathfrak{sl}_3^{e_{\mathrm{subreg}}}$, which is two-dimensional,
and the normal ordering produces only quadratic corrections.  For
$n \ge 4$, the slice dimension grows and the screening-mediated
normal-ordering corrections introduce genuinely new cubic, quartic,
$\dots$, $(n-1)$-ary terms.  The subregular family thus traces
the transition from classical to homotopical Koszul duality,
parameterized by the simplest geometric invariant: the dimension of
the Slodowy slice.
\end{remark}
