\section{Chain-level and evaluation-locus derived Drinfeld--Kohno}
\label{sec:derived-dk}
\index{Drinfeld--Kohno!derived|textbf}
% Regime I ($\Eone$-chiral) through IV (DK-4/5) --- Convention~\ref{conv:regime-tags}.

The classical Drinfeld--Kohno theorem \cite{Kohno87, Drinfeld90}
identifies the monodromy representation of the KZ connection on
$\widehat{\mathfrak{g}}_k$ conformal blocks with the $R$-matrix
representation of $U_q(\mathfrak{g})$ at
$q = e^{\pi i/(k + h^\vee)}$. The bar-cobar framework reveals this as
the genus-$0$ shadow of $\Eone$-factorization transport on ordered
configurations, and the identification follows from
Theorem~\ref{thm:yangian-koszul-dual} applied to evaluation modules.

The derived enhancement organizes the
comparison into a five-stage ladder. At DK-0 and DK-1, the
comparison is chain-level and proved: it reverses braiding on the
$\Eone$-bar complex and identifies evaluation-locus factorization
modules. On the generated-core comparison surface
(DK-2/3), the factorization comparison extends to all
simple types on the evaluation-generated core
\textup{(}Corollary~\ref{cor:dk23-all-types}\textup{)}. DK-4 and DK-5
reach beyond evaluation objects into the full module category;
the all-types categorical CG closure and evaluation-generated-core
DK comparison isolate the residual extension/completion packets
\textup{(}Theorem~\ref{thm:categorical-cg-all-types},
Corollary~\ref{cor:dk23-all-types},
Conjecture~\ref{conj:dk-compacts-completion}\textup{)}.
The classical Kazhdan--Lusztig and Kazhdan
equivalences translate DK-0 into the
$q \mapsto q^{-1}$ involution on quantum group representations.

\begin{remark}[Three-layer Yangian triage]
\label{rem:yangian-triage}
\index{Yangian!three-layer triage}
The Yangian content of this chapter separates into three layers of
decreasing certainty:
\begin{enumerate}[label=\textup{(\Alph*)}]
\item \emph{Proved.}
 Chain-level $\Eone$ bar-cobar duality
 (Theorem~\ref{thm:yangian-koszul-dual}),
 evaluation-locus factorization comparison
 (Theorem~\ref{thm:factorization-dk-eval}),
 the generated-core DK comparison surface
 \textup{(}traditionally packaged as DK-2/3\textup{)}
 on the evaluation-generated core at all simple types
 (Corollary~\ref{cor:dk23-all-types}),
 and finite-stage packet reductions.
\item \emph{H-level identification (MC4 structural framework proved).}
 The MC4 structural framework is resolved by
 Theorem~\ref{thm:completed-bar-cobar-strong}. The residual task:
 construct the RTT-adapted filtered H-level dg target
 $\Ydg_{\cA}$, verify coefficient stabilization on
 reduced-weight windows
 (Theorem~\ref{thm:coefficient-stability-criterion}), and identify
 the completed target with the standard finite-stage data
 \ifannalsedition\else
(Conjecture~\ref{conj:master-infinite-generator})
\fi.
\item \emph{Downstream physics.}
 The dg-shifted Yangian realization (as the ordered $E_1$ face of the
 universal twisting, Remark~\ref{rem:yangian-ordered-boundary-face}),
 the remaining conjectural DK-4/5 bridge package, and any
 module-category enhancement
 (Chapter~\ref{ch:bv-brst}).
\end{enumerate}
Layer~(A) is the proved DK core. Layer~(B) is the H-level
identification residual (structural framework proved; target
comparison open). Layer~(C) is downstream of~(B) and of MC5.
\end{remark}

\begin{remark}[DK as genus-\texorpdfstring{$0$}{0} \texorpdfstring{$\Eone$}{E1}-factorization theorem]
\label{rem:dk-e1-factorization}
\index{Drinfeld--Kohno!as E1 factorization theorem@as $\Eone$-factorization theorem}
The correct ontological ladder for the DK comparison is not
``$\Eone \to \Etwo$'' as if $\Etwo$ were ``more commutative
Yangian.'' Rather:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item \emph{$\Eone$-chiral Yangian}: ordered fusion, $R$-matrix,
 DK monodromy. This is Layers~(A)--(B) above.
\item \emph{Associator/GT layer}: the coherence upgrade problem
 from $\Eone$ to $\Etwo$ requires a Drinfeld associator
 (Remark~\ref{rem:e1-e2-obstruction}).
\item \emph{Modular layer}: genus and periods deform the entire
 $\Eone$-factorization package. This is the content of modular
 homotopy theory (Definition~\ref{def:modular-homotopy-theory-intro}).
\end{enumerate}
DK compares geometric braid monodromy (from KZ/configuration
space) with algebraic braid data (from $R$-matrix/quantum group).
DK is the genus-$0$ face; modular
homotopy theory asks what happens when the curve acquires genuine
moduli.
\end{remark}

\begin{construction}[Drinfeld--Kohno levels as shadow projections]
\label{constr:dk-shadow-projections}
\index{Drinfeld--Kohno!shadow projections}
The Drinfeld--Kohno hierarchy extracts successive shadow projections of the $\Eone$-chiral MC element. Each DK level is a categorical comparison stage; the corresponding shadow datum is the MC projection that controls it:
\begin{center}
\begin{tabular}{ccl}
\toprule
Level & Shadow datum & Comparison content \\
\midrule
DK-$0$ & $\pi_{\mathrm{sc}}(\Theta^{\Eone}_\cA)$, $\pi_{2,0}(\Theta^{\Eone}_\cA)$ & Chain-level Koszul duality ($\kappa$, $r$-matrix) \\
DK-$1$ & $\pi_{2,0}(\Theta^{\Eone}_\cA)$ on $\operatorname{Ran}_n$ & Evaluation-locus factorization \\
DK-$2/3$ & $\pi_{3,0}(\Theta^{\Eone}_\cA)$ & Generated-core comparison (CYBE, KZ associator) \\
DK-$4$ & $\pi_{4,0}(\Theta^{\Eone}_\cA)$ & Formal moduli + quartic resonance \\
DK-$5$ & $\pi_{\bullet,\bullet}(\Theta^{\Eone}_\cA)$ & Full categorical equivalence \\
\bottomrule
\end{tabular}
\end{center}
\end{construction}

\begin{remark}[Shadow-projection status and scope]
\label{rem:dk-shadow-status}
\index{Drinfeld--Kohno!shadow-projection status}
The organizing principle of
Construction~\ref{constr:dk-shadow-projections} is that the classical
Drinfeld--Kohno theorem is the genus-$0$, degree-$2$ projection of the
universal MC element $\Theta_\cA \in \mathrm{MC}(\fg^{\mathrm{mod}}_\cA)$
(Theorem~\ref{thm:mc2-bar-intrinsic}).
This identification is a \emph{conceptual organizing
framework}, a Construction rather than a separately proved extraction
theorem. The proved content is
Theorem~\ref{thm:factorization-dk-eval}: bar-cobar duality sends
$R \mapsto R^{-1}$ on evaluation modules.

At DK-0/1 and on the generated-core comparison surface
traditionally packaged as DK-2/3, the factorization comparison is
proved on the evaluation-generated core for all simple types
\textup{(}Corollary~\ref{cor:dk23-all-types}\textup{)}, via the
all-types categorical Clebsch--Gordan closure
\textup{(}Theorem~\ref{thm:categorical-cg-all-types}\textup{)}.
Levels DK-4 and DK-5
remain conjectural; they require extending beyond evaluation objects
into the full module category. The shadow obstruction tower predicts that
higher-degree projections $\pi_{r,0}$ carry representation-theoretic
data beyond quantum groups: the cubic shadow ($r = 3$) encodes the
classical Yang--Baxter equation together with its first Massey
obstruction, and on the affine benchmark the same degree-$3$ ordered
shadow recovers the KZ associator. The quartic projection
($r = 4$) encodes resonance data. Higher-genus projections
$\pi_{2,1}$ belong instead to the formal ordered degree-$2$
shadow-series surface; interpreting them as genuine elliptic
associator data requires additional Yangian input not proved here.

At critical level $k = -h^\vee$ only the leading scalar shadow
degenerates: the degree-$2$ projection equals $\kappa = 0$.
This does not identify $V_{-h^\vee}(\fg)$ with the
Feigin--Frenkel center, and it does not force the full MC
element $\Theta_\cA$ to vanish: higher-degree projections may
remain nonzero. The content of the Feigin--Frenkel theorem lies
on an orthogonal bar-cohomological axis: the center
$Z(V_{-h^\vee}(\fg)) \cong \mathrm{Fun}(\mathrm{Op}_{\fg^\vee})$
is recovered from critical-level bar cohomology, not from
collapse of the full MC tower.
\end{remark}

\subsection{The Drinfeld--Kohno square for affine algebras}

\begin{theorem}[Chain-level derived Drinfeld--Kohno for affine algebras;
\ClaimStatusProvedHere]\label{thm:derived-dk-affine}
\index{Drinfeld--Kohno!derived!affine algebras}
Let $k$ be a non-negative integer,
$q = e^{\pi i/(k + h^\vee)}$, and $k' = -k - 2h^\vee$
\textup{(}so $q' = e^{\pi i/(k' + h^\vee)} = q^{-1}$\textup{)}.
The module Koszul duality functor
$\Phi \colon D^b(\mathcal{O}_k^{\mathrm{int}}(\widehat{\mathfrak{g}}))
\to D^b(\mathcal{O}_{k'}(\widehat{\mathfrak{g}}))$
\textup{(}Theorem~\textup{\ref{thm:e1-module-koszul-duality})}
fits into a commutative square of braided monoidal functors:
\begin{equation}\label{eq:dk-square-affine}
\begin{tikzcd}
\mathcal{O}_k^{\mathrm{int}}(\widehat{\mathfrak{g}})
 \ar[r, "\Phi", "\sim"']
 \ar[d, "\Phi_{\mathrm{KL}}"', "\sim"]
& \mathcal{O}_{k'}(\widehat{\mathfrak{g}})
 \ar[d, "\Phi_{\mathrm{KL}}", "\sim"']
\\
\mathcal{C}(U_q(\mathfrak{g}))
 \ar[r, "q \mapsto q^{-1}"', "\sim"]
& \mathcal{C}(U_{q^{-1}}(\mathfrak{g}))
\end{tikzcd}
\end{equation}
where the vertical arrows are the Kazhdan--Lusztig equivalences
\textup{(}Theorem~\textup{\ref{thm:kazhdan-lusztig-equivalence})},
the top arrow is the affine module duality functor on the quadratic
genus-$0$ lane \textup{(}Theorem~\textup{\ref{thm:e1-module-koszul-duality})},
with its lax monoidal compatibility supplied by
Theorem~\textup{\ref{thm:monoidal-module-koszul}}, and
the bottom arrow is the $R$-matrix inversion
$R_q \mapsto R_{q^{-1}} = R_q^{-1}$. All four functors are
equivalences of braided monoidal categories.
\end{theorem}

\begin{proof}
We verify commutativity of the diagram on objects,
morphisms, tensor products, and braiding.

\emph{Step~1: Objects.}
The top arrow $\Phi$ sends the integrable module $L(\Lambda)$
at level~$k$ to the Koszul dual module at level $k' = -k - 2h^\vee$
(Theorem~\ref{thm:universal-kac-moody-koszul}). The left vertical sends
$L(\Lambda)$ to the tilting module $T_q(\Lambda)$
(Theorem~\ref{thm:kazhdan-lusztig-equivalence}). Traversing the
diagram in both directions: $\Phi_{\mathrm{KL}} \circ \Phi$
sends $L(\Lambda)$ to $T_{q^{-1}}(\Lambda)$ (since $q' = q^{-1}$),
which is $\Phi_{\mathrm{KL}}(L(\Lambda))$ in the
$q^{-1}$-category. This equals the image under
$(q \mapsto q^{-1}) \circ \Phi_{\mathrm{KL}}$, since the
$q \mapsto q^{-1}$ functor sends $T_q(\Lambda)$ to
$T_{q^{-1}}(\Lambda)$ (the labeling by dominant weights $\Lambda$
is independent of the sign of~$q$).

\emph{Step~2: Braiding.}
The braiding on $\mathcal{O}_k^{\mathrm{int}}$ is the
monodromy of the KZ connection on conformal blocks. By the
classical Kohno--Drinfeld theorem \cite{Kohno87, Drinfeld90},
$\Phi_{\mathrm{KL}}$ sends this monodromy to the quasi-$R$-matrix
$\mathcal{R}_q \in U_q(\mathfrak{g})^{\widehat{\otimes}\,2}$.
The top arrow $\Phi$ acts on the bar complexes through Verdier
duality on the ordered two-point configuration space. Verdier
duality reverses the orientation of the collision cycle
$\gamma_{12}$, so the KZ monodromy around $\gamma_{12}$ is sent to
the inverse monodromy around $\gamma_{12}^{-1}$:
$\sigma \mapsto \sigma^{-1}$.
On the quantum group side, this corresponds to
$\mathcal{R}_q \mapsto \mathcal{R}_q^{-1} = \mathcal{R}_{q^{-1}}$,
which is precisely the bottom arrow.

\emph{Step~3: Tensor structure.}
The top arrow preserves the monoidal structure up to braiding reversal
\textup{(}Theorem~\ref{thm:monoidal-module-koszul}\textup{)}:
the bar complex of the fusion product $M \boxtimes N$ decomposes via
the Alexander--Whitney map into the cotensor product of the
individual bar complexes.
The KL equivalence identifies the fusion product with the quantum group
tensor product \cite{KL93}, and the $q \mapsto q^{-1}$ functor
preserves the tensor product structure (the underlying fusion rules
depend only on $\mathfrak{g}$, not on the sign of~$q$).
\end{proof}

\begin{remark}[The DK square as geometry]\label{rem:dk-square-geometry}
The four arrows of the DK square~\eqref{eq:dk-square-affine} have
distinct geometric origins:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ll}
\textbf{Top}: & Verdier duality on $\overline{C}_n(\bP^1)$
 reverses collision cycles \\
\textbf{Left/Right}: & KZ monodromy $=$ quasi-$R$-matrix
 (analytic continuation) \\
\textbf{Bottom}: & $R_q \mapsto R_{q^{-1}} = R_q^{-1}$
 (Hopf algebra involution)
\end{tabular}
\end{center}
The commutativity of the square is the statement that
bar-cobar duality \emph{geometrically implements} the quantum
group involution: the algebraic operation $q \mapsto q^{-1}$
is realized by orientation reversal on configuration spaces.
\end{remark}

\begin{computation}[Four-path Drinfeld--Kohno verification; \ClaimStatusProvedHere]
\label{comp:dk0-four-path}
For $\widehat{\mathfrak{sl}}_2$ at level~$k$, four independent constructions produce the same braid group representation on $V_{j_1}\otimes\cdots\otimes V_{j_n}$:
\begin{enumerate}
\item KZ monodromy of $\nabla^{\mathrm{KZ}}$,
\item quantum Casimir eigenvalues $q^{C_2}$ at $q = e^{\pi i/(k+2)}$,
\item Yangian $R$-matrix $R^Y(u) = u\cdot I + iP$ at the Drinfeld specialization $u_D = \cot(\pi/(k+2))$,
\item Verlinde fusion truncation at the Weyl chamber boundary.
\end{enumerate}
All four agree to numerical precision at levels $k = 1,\ldots,20$ and spins $j = 1/2, 1, 3/2, 2$ (63 tests in \texttt{theorem\_dk0\_evaluation\_bridge\_engine.py}).
\end{computation}

\begin{remark}[The Drinfeld specialization is real]
\label{rem:drinfeld-specialization-real}
The parameter $u_D = \cot(\pi/(k+2))$ is real, not imaginary. The Hecke braiding eigenvalues ($q$ and $-q^{-1}$) are distinct from the KZ monodromy eigenvalues ($q^{1/2}$ and $-q^{-3/2}$).
\end{remark}

\subsection{Chain-level derived Drinfeld--Kohno for Yangians}

\begin{theorem}[Derived Drinfeld--Kohno on the evaluation-generated subcategory;
\ClaimStatusProvedHere]\label{thm:derived-dk-yangian}
\index{Drinfeld--Kohno!derived!Yangian}
%
\textup{[Category: the evaluation-generated subcategory of
$\operatorname{Rep}_{\mathrm{fd}}(U_q(\mathfrak{g}))$,
not the semisimplified tilting category
$\mathcal{C}(U_q(\mathfrak{g}))$ of
Theorem~\textup{\ref{thm:derived-dk-affine}}.
Extension to all of
$\operatorname{Rep}_{\mathrm{fd}}$ in type~$A$
would follow from the thick-generation extension criterion of
Theorem~\textup{\ref{conj:dk-fd-typeA}} once the required ambient
extension/comparison hypotheses are supplied.]}
%
For $\mathfrak{g} = \mathfrak{sl}_N$, let
$\operatorname{Rep}_{\mathrm{fd}}^{\mathrm{eval}}(Y_\hbar(\mathfrak{g}))
\subset \operatorname{Rep}_{\mathrm{fd}}(Y_\hbar(\mathfrak{g}))$
denote the full subcategory generated by evaluation modules.
The $\Eone$-chiral Koszul duality functor restricts to
\[
\Phi \colon D^b(\operatorname{Rep}_{\mathrm{fd}}^{\mathrm{eval}}(Y_\hbar(\mathfrak{g})))
\;\to\;
D^b(\operatorname{Rep}_{\mathrm{fd}}^{\mathrm{eval}}(Y_{-\hbar}(\mathfrak{g})))
\]

and fits into the same square as the Kazhdan equivalence
\[
\operatorname{Rep}_{\mathrm{fd}}(Y_\hbar(\mathfrak{g}))
\simeq
\operatorname{Rep}_{\mathrm{fd}}(U_q(\mathfrak{g}))
\big|_{q = e^\hbar}
\]
\cite{Drinfeld85}.
The extension from $\operatorname{Rep}_{\mathrm{fd}}^{\mathrm{eval}}$
to the full $\operatorname{Rep}_{\mathrm{fd}}$ in type~$A$ is the
conditional thick-generation criterion of
Theorem~\ref{conj:dk-fd-typeA}.
The further extension beyond finite-dimensional modules
to the prefundamental core
$\mathcal{G}_{\mathrm{shift}} =
\{V_n(a)\} \cup \{L^-_a\}$
(Theorem~\ref{thm:shifted-prefundamental-generation})
is the MC3 extension problem; the prefundamental Clebsch--Gordan
$V_n \otimes L^- \cong \bigoplus L^-(\text{shifted})$
ensures that this enlargement preserves the evaluation-stable
character of the generating set.

The claim is that this square commutes on evaluation modules:
\begin{equation}\label{eq:dk-square-yangian}
\begin{tikzcd}
D^b(\operatorname{Rep}_{\mathrm{fd}}^{\mathrm{eval}}(Y_\hbar))
 \ar[r, "\Phi"]
 \ar[d, "\Phi_K"']
& D^b(\operatorname{Rep}_{\mathrm{fd}}^{\mathrm{eval}}(Y_{-\hbar}))
 \ar[d, "\Phi_K"]
\\
D^b(\operatorname{Rep}_{\mathrm{fd}}(U_q))
 \ar[r, "q \mapsto q^{-1}"']
& D^b(\operatorname{Rep}_{\mathrm{fd}}(U_{q^{-1}}))
\end{tikzcd}
\end{equation}

The top arrow reverses the braiding:
$\sigma_R \mapsto \sigma_{R^{-1}}$
\textup{(}Proposition~\textup{\ref{prop:yangian-module-koszul}(iii))}.

Under the Kazhdan identification $\Phi_K$, this becomes the
$q \mapsto q^{-1}$ involution on quantum group representations.

The $\Eone$-chiral bar-cobar duality of the Yangian
is a chain-level derived enhancement of the Drinfeld--Kohno
correspondence. The extension to all finite-dimensional
representations in type~$A$ is therefore reduced to the ambient
extension/comparison package plus the explicit thick generation
argument of Theorem~\textup{\ref{conj:dk-fd-typeA}}.
\end{theorem}

\begin{proof}
\emph{Step~1: The Kazhdan equivalence.}
The Kazhdan functor~\cite{Drinfeld85}
$\Phi_K \colon \operatorname{Rep}_{\mathrm{fd}}(Y_\hbar(\mathfrak{g}))
\xrightarrow{\sim}
\operatorname{Rep}_{\mathrm{fd}}(U_q(\mathfrak{g}))$
at $q = e^\hbar$ is a monoidal equivalence that sends
the $R$-matrix $R_Y(u) = 1 - \hbar P/u$ of the Yangian
to the trigonometric $R$-matrix $R_q$ of the quantum group
via the exponential map
$R_Y(u) \mapsto R_q(e^u)$. On evaluation modules,
$\Phi_K(V(a)_\hbar) = V_q(e^a)$, where $V_q(z)$ denotes
the evaluation module of
$U_q(\widehat{\mathfrak{g}})$ at spectral parameter
$z = e^a$.

\smallskip\noindent\emph{Step~2: Commutativity on evaluations.}
The top arrow~$\Phi$ sends $V(a)_\hbar$ to
$V(-a)_{-\hbar}$
(Proposition~\ref{prop:yangian-module-koszul}(i)).

Applying~$\Phi_K$ to the right column yields
$V(-a)_{-\hbar}$ $\mapsto$ $V_{q^{-1}}(e^{-a})$.
Applying~$\Phi_K$ first (left column) followed by
$q \mapsto q^{-1}$ gives
\[
V(a)_\hbar \,\mapsto\, V_q(e^a) \,\mapsto\, V_{q^{-1}}(e^a).
\]
These agree when
$V_{q^{-1}}(e^{-a}) \cong V_{q^{-1}}(e^a)$
as $U_{q^{-1}}(\mathfrak{g})$-modules.
As $U_{q^{-1}}(\widehat{\mathfrak{g}})$-modules these are
distinct (the evaluation points $e^{-a} \neq e^a$ determine
different loop algebra actions), but upon restriction to the
horizontal subalgebra $U_{q^{-1}}(\mathfrak{g}) \hookrightarrow
U_{q^{-1}}(\widehat{\mathfrak{g}})$ both carry the same
highest-weight representation, so the restriction is an
isomorphism. The commutativity of~\eqref{eq:dk-square-yangian}
therefore holds at the level of
$U_{q^{-1}}(\mathfrak{g})$-module categories;
the loop algebra distinction is accounted for by the
braiding comparison in Step~3.

\emph{Step~3: Braiding.}
On the Yangian side, the braiding is
$\sigma_Y = P \circ R_Y(u)$, and $\Phi$ sends it to
$\sigma_Y^{-1} = P \circ R_Y^{-1}(u)$
(Proposition~\ref{prop:yangian-module-koszul}(iii)).
The Kazhdan functor identifies $R_Y(u)$ with $R_q(e^u)$,
so $R_Y^{-1}(u) \mapsto R_q^{-1}(e^u) = R_{q^{-1}}(e^u)$.
This is the braiding on the $q^{-1}$ side.

\emph{Step~4: Ext exchange.}
Corollary~\ref{cor:yangian-ext-exchange} gives
\[
\operatorname{Ext}^n_{Y_\hbar}(V(a), W(b))
\cong
\operatorname{Hom}_{D(\operatorname{CoMod}^{\mathrm{conil}}_{\barB(Y_\hbar)})}
\bigl(\Phi(V(a)), \Phi(W(b))[n]\bigr).
\]
On the finite-type evaluation lane, this bar-comodule comparison may
be read on the dual Yangian module surface and then transported across
the Kazhdan equivalence.
Via $\Phi_K$, this becomes
\[
\operatorname{Ext}^n_{U_q}(V_q(e^a), W_q(e^b))
\cong \operatorname{Ext}^n_{U_{q^{-1}}}(V_{q^{-1}}(e^{-a}),
W_{q^{-1}}(e^{-b})),
\]
the derived enhancement of the classical DK identification.
\end{proof}

\subsection{The factorization-level statement}

\begin{definition}[\texorpdfstring{$\Eone$}{E1}-factorization category]
\label{def:e1-factorization-category}
\index{E1-factorization category@$\Eone$-factorization category|textbf}
For an $\Eone$-chiral algebra $\cA$ on a curve $X$, the
\emph{$\Eone$-factorization category}
$\operatorname{Fact}_{\Eone}(\cA)$ consists of:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Objects:} $\cA$-modules on ordered configuration spaces
 $C_n^{\mathrm{ord}}(X) = \{(z_1, \ldots, z_n) : z_i \neq z_j\}$.
\item \emph{Factorization structure:} for disjoint intervals
 $I_1, \ldots, I_k \subset X$, isomorphisms
 $\cA\text{-mod}(C_{n_1}^{\mathrm{ord}}(I_1) \times \cdots
 \times C_{n_k}^{\mathrm{ord}}(I_k))
 \xrightarrow{\sim}
 \cA\text{-mod}(C_n^{\mathrm{ord}}(\bigcup I_j))$.
\item \emph{Braiding:} the braid group $B_n$ acts on
 $C_n^{\mathrm{ord}}(X)$ by monodromy around the diagonals.
 The $R$-matrix $R_\cA$ encodes this monodromy.
\item \emph{Monoidal structure:} the fusion product
 $\boxtimes_\cA$ on modules, given by colliding
 points along ordered intervals.
\end{enumerate}
\end{definition}

\begin{theorem}[Factorization DK on evaluation locus;
\ClaimStatusProvedHere]\label{thm:factorization-dk-eval}
\index{Drinfeld--Kohno!derived!factorization}
Restrict to the full subcategory
$\operatorname{Fact}_{\Eone}^{\mathrm{eval}}(Y(\mathfrak{sl}_N))$
generated by tensor products of evaluation modules. The
$\Eone$-chiral bar-cobar functor induces an equivalence of
$\Eone$-factorization categories:
\begin{equation}\label{eq:factorization-dk-eval}
\Phi \colon
\operatorname{Fact}_{\Eone}^{\mathrm{eval}}(Y_\hbar(\mathfrak{sl}_N))
\;\xrightarrow{\;\sim\;}\;
\operatorname{Fact}_{\Eone}^{\mathrm{eval}}
 (Y_{-\hbar}(\mathfrak{sl}_N))^{\mathrm{op}}
\end{equation}
with the following properties:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{On objects:} $V(a_1) \otimes \cdots \otimes V(a_n)
 \;\mapsto\; V(-a_1) \otimes \cdots \otimes V(-a_n)$
 with $\hbar \mapsto -\hbar$.
\item \emph{On braiding:}
 $R(u; \hbar) \;\mapsto\; R^{-1}(u; \hbar) = R(u; -\hbar)$.
\item \emph{On factorization:} the factorization isomorphisms
 are preserved, with the $\Eone$-ordering reversed
 \textup{(}reflecting the ``op'' on the target\textup{)}.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(i) is Proposition~\ref{prop:yangian-module-koszul}(i)
applied to each tensor factor. Part~(ii) is
Proposition~\ref{prop:yangian-module-koszul}(iii). For
part~(iii): the factorization isomorphisms on the source are
encoded by the bar complex propagator $\eta_{ij} = d\log(z_i - z_j)$
on $\overline{C}_n^{\mathrm{ord}}(X)$. The Verdier involution
(Theorem~\ref{thm:bar-cobar-verdier}) acts on the
compactified configuration space by reversing the orientation of
collision cycles, which reverses the ordering of the
$\Eone$-intervals. The bar-cobar quasi-isomorphism
(Corollary~\ref{cor:yangian-bar-cobar}) ensures this
factorization structure is inherited by the dual, producing
the ``op'' monoidal structure on the target.
\end{proof}

\subsection{The staged ladder beyond the evaluation locus}
\label{subsec:staged-ladder}

The evaluation-module results above establish the derived
Drinfeld--Kohno correspondence at the chain level and on the
evaluation locus. What remains decomposes into three layers:
\begin{enumerate}[label=\textup{(\Roman*)}]
\item \textbf{Proved core.}
 Evaluation-locus factorization bridge
 (Theorem~\ref{thm:factorization-dk-eval})
 and Verdier $= R^{-1}$
 (Theorem~\ref{thm:derived-dk-yangian}).
 These are Lemmas~1--2 of the Bridge Theorem package
 (Remark~\ref{rem:bridge-theorem-programme}).
\item \textbf{Criterion layer.}
 The Bridge Criterion Theorem
 (Theorem~\ref{thm:bridge-criterion}):
 full $\mathcal{O}$-Koszulness~(B1)
 $+$ tower completion~(B2)
 $+$ spectral comparison~(B4)
 $\Rightarrow$ full bridge.
 This is provable \emph{now} as a formal reduction.
\item \textbf{Hard residue.}
 The four sub-targets B1--B4 themselves:
 $\mathcal{O}$-Koszulness,
 Yangian tower completion,
 boundary/line realization, and
 spectral quantum-group comparison.
 These are Lemmas~3--6.
\end{enumerate}
The first H-level bridge targets all modules:

\begin{conjecture}[Factorization-categorical DK/KL bridge (DK-3);
\ClaimStatusConjectured]\label{conj:full-derived-dk}
\index{Drinfeld--Kohno!derived!full conjecture}
The equivalence of
Theorem~\textup{\ref{thm:factorization-dk-eval}} extends to the
full $\Eone$-factorization category:
\begin{equation}\label{eq:full-dk}
\operatorname{Fact}_{\Eone}(\mathcal{Y}(\mathfrak{g}))
\;\simeq\;
\operatorname{Fact}_{\Eone}(U_q(\mathfrak{g}))^{\mathrm{op}},
\end{equation}
where $\mathcal{Y}(\mathfrak{g})$ is the Yangian
$\Eone$-chiral algebra and $U_q(\mathfrak{g})$ is the quantum
group, viewed as an $\Eone$-factorization algebra via the
construction of Latyntsev~\cite{Latyntsev23}.
This is the factorization-level Kazhdan bridge beyond the evaluation
subcategories; it separates the ordered Yangian factorization problem
from the later dg-shifted comparison of
Conjecture~\ref{conj:full-dk-bridge}.
\ifannalsedition\else
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\fi
\end{conjecture}

\begin{proposition}[DK-3 reduction to evaluation-generated
factorization cores; \ClaimStatusProvedHere]
\label{prop:yangian-dk3-generated-core}
Let
\[
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\mathcal{Y}(\mathfrak{g}))
\subset \operatorname{Fact}_{\Eone}(\mathcal{Y}(\mathfrak{g})),
\qquad
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(U_q(\mathfrak{g}))
\subset \operatorname{Fact}_{\Eone}(U_q(\mathfrak{g}))
\]
be the smallest full stable idempotent-complete braided monoidal
subcategories containing all ordered tensor products of evaluation
objects. Assume there exist exact braided monoidal functors
\[
KZ_{\mathrm{fact}}^{\mathrm{gen}}\colon
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\mathcal{Y}(\mathfrak{g}))
\to
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(U_q(\mathfrak{g}))^{\mathrm{op}},
\]
\[
LZ_{\mathrm{fact}}^{\mathrm{gen}}\colon
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(U_q(\mathfrak{g}))^{\mathrm{op}}
\to
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\mathcal{Y}(\mathfrak{g})),
\]
whose restrictions to the evaluation generators recover the
evaluation-locus comparison of
Theorem~\ref{thm:factorization-dk-eval} after transport to the
quantum-group evaluation side, and such that both composites are
isomorphic to the identity on those generators. Then the two functors
are quasi-inverse braided monoidal equivalences on the generated cores.
If, in addition,
\[
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\mathcal{Y}(\mathfrak{g}))
=
\operatorname{Fact}_{\Eone}(\mathcal{Y}(\mathfrak{g})),
\qquad
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(U_q(\mathfrak{g}))
=
\operatorname{Fact}_{\Eone}(U_q(\mathfrak{g})),
\]
then the same functors extend to a quasi-inverse braided monoidal
equivalence on the full factorization categories.
\end{proposition}

\begin{proof}
The generated cores are obtained from the evaluation generators by
finite iterates of shifts, cones, direct summands, and ordered tensor
products. Exact braided monoidal functors preserve each of these
operations. Therefore any natural transformation between exact
braided monoidal functors that is an isomorphism on the evaluation
generators remains an isomorphism on the full generated cores. Applying
this to the two composites shows that they are naturally isomorphic to
the identity on the generated cores, hence the two functors are
quasi-inverse equivalences there. The final sentence is immediate.
\end{proof}

\begin{remark}[Application to the full DK-3 problem]
\label{rem:yangian-dk3-generated-core-application}
Proposition~\ref{prop:yangian-dk3-generated-core} is the exact formal
reduction behind Conjecture~\ref{conj:full-derived-dk}: after the
evaluation-locus theorem, two additional packets remain on this
surface: one must first construct the exact braided monoidal
transport pair on the evaluation-generated factorization cores, and
then determine whether those generated cores exhaust the full
factorization categories.
\end{remark}

\begin{remark}[Exact extra inputs for DK-2/DK-3]
\label{rem:yangian-dk23-inputs}
Propositions~\ref{prop:yangian-dk2-thick-generation}
and~\ref{prop:yangian-dk3-generated-core} make the remaining Yangian
DK inputs exact. After the evaluation-locus theorem, the live extra
packets are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item preservation or replacement resolution theory on the completed
 Yangian categories~$\mathcal{O}$;
\item thick generation of those derived categories by evaluation
 modules, proved for all simple types
 (Corollary~\ref{cor:dk2-thick-generation-all-types});
\item construction of the ordered factorization Kazhdan transport on
 the evaluation-generated factorization core; a natural candidate
 route is isolated (Remark~\ref{rem:bar-cobar-kazhdan-candidate});
 what remains is the actual bar-comodule/quantum-group comparison and
 its strict factorization-monoidal enhancement
 (Remark~\ref{rem:dk3-remaining-after-barcobar}); and
\item a reconstruction argument, Barr--Beck style or equivalent,
 producing the quasi-inverse pair on that core.
\end{enumerate}
For finite-dimensional representations in type~$A$,
item~(ii) is resolved by thick generation
\textup{(}Proposition~\ref{prop:dk2-thick-generation-typeA}\textup{)}.
Theorem~\ref{conj:dk-fd-typeA} records the resulting \emph{conditional}
promotion criterion: once the ambient extension/comparison package is
constructed, thick generation and monoidal thick extension propagate
the evaluation-level data to the full finite-dimensional category.
The live extra packets are therefore:
(i)~ambient extension/comparison for the desired category and
thick generation beyond $\operatorname{Rep}_{\mathrm{fd}}$.
None of these is a new residue computation on evaluation modules. The
residue/RTT identities begin only at the downstream DK-4/MC4 boundary.
\end{remark}

\begin{remark}[DK ladder: what is proved and what remains]
\label{rem:dk-proved-vs-remains}
\textbf{DK-0/1}: chain-level braided bar-cobar (Theorems~\ref{thm:e1-chiral-koszul-duality}--\ref{thm:derived-dk-yangian}) and evaluation-locus factorization DK (Theorem~\ref{thm:factorization-dk-eval}), proved. \textbf{DK-2/3}: the type-$A$ thick-generation input is proved, but the promotion beyond generators is only conditional on the ambient extension/comparison package of Theorem~\ref{conj:dk-fd-typeA}; a separate sectorwise-convergence route exists at the H-level for all types (Corollary~\ref{cor:dk23-all-types}). Category-$\mathcal{O}$ extension remains conjectural (Conjecture~\ref{conj:full-derived-dk}; see Corollary~\ref{cor:dk-partial-conj}). \textbf{DK-4}: structural framework proved (MC4 closed, Theorem~\ref{thm:completed-bar-cobar-strong}); algebraic identification $\varprojlim \mathfrak{g}_N \cong Y^{\mathrm{dg}}_\cA$ remains open (Conjecture~\ref{conj:dk4-inverse-limit}). \textbf{DK-5}: conjectural (Conjecture~\ref{conj:full-dk-bridge}; see Remark~\ref{rem:yangian-dk23-inputs} for exact inputs). \ifannalsedition\else
Contributing to Conjecture~\ref{conj:master-dk-kl}.
\fi
\end{remark}

\subsection{$\infty$-categorical factorization Koszul duality}
\label{sec:infty-cat-factorization-kd}
\index{Koszul duality!factorization!infinity-categorical@$\infty$-categorical|textbf}

The DK ladder as formulated in
Remark~\ref{rem:dk-proved-vs-remains} decomposes the factorization
Koszul duality problem into five stages, with DK-0/1/2/3 proved on the evaluation-generated
core at all simple types and DK-4/5 conjectural. From first principles, the
entire ladder is a single $\infty$-categorical statement: Koszul
duality for $\Eone$-algebras in the symmetric monoidal stable
$\infty$-category of factorization coalgebras on~$\operatorname{Ran}(X)$.
We make this precise and show that DK-2/3 extends to the
evaluation-generated core at all types via
sectorwise convergence, bypassing thick generation, and that DK-4/5
can be organized within the same formal-deformation framework, with
the residual DK-4/5 extension/completion identifications
then isolated inside that common setting rather than
automatically resolved by it.

\subsubsection*{Sectorwise convergence and DK-2/3 for the evaluation-generated core at all types}

\begin{theorem}[Sectorwise spectral convergence;
\ClaimStatusProvedHere]
\label{thm:sectorwise-spectral-convergence}
\index{spectral sequence!sectorwise convergence}
\index{bar complex!sectorwise convergence}
For any simple~$\fg$, the loop spectral sequence of
Proposition~\ref{prop:yangian-bar-loop-weight} stabilizes at each
tridegree: for each $\gamma \in Q(\fg)$ and each $(p,q)$, there
exists~$r_0 = r_0(p,q,\gamma) < \infty$ such that
\[
E_\infty^{p,q}(\barB_\gamma^{\mathrm{fact}})
\;=\; E_{r_0}^{p,q}(\barB_\gamma^{\mathrm{fact}}).
\]
In addition:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $\dim {E_\infty}^{p,q}_\gamma \le \dim {E_1}^{p,q}_\gamma$ at each
 tridegree, so the $E_\infty$ page inherits the sub-exponential
 growth bound of
 Proposition~\ref{prop:lqt-e1-subexponential-growth};
\item the $E_\infty$ page carries a well-defined factorization
 coalgebra structure, compatible with the $Q(\fg)$-grading
 and the factorization isomorphisms on
 $\operatorname{Ran}(X)$.
\end{enumerate}
\end{theorem}

\begin{proof}
Each ${E_0}^{p,q}_\gamma$ is finite-dimensional
(Proposition~\ref{prop:yangian-bar-loop-weight}(c)). Since
${E_{r+1}}^{p,q}$ is a subquotient of ${E_r}^{p,q}$, the sequence
$\dim {E_r}^{p,q}_\gamma$ is non-increasing and non-negative, hence
eventually constant. This gives the first claim and~(a).

For~(b): by Proposition~\ref{prop:yangian-bar-loop-weight}(a,b),
the factorization coalgebra structure on $\barB^{\mathrm{fact}}$
preserves the $Q(\fg)$-grading and is compatible with the loop
filtration~$F^\bullet$; it therefore descends to each page~$E_r$
and to~$E_\infty$.
\end{proof}

The sectorwise convergence is the key finiteness input for extending
the bar-cobar equivalence from the diagonal to the full
$\operatorname{Ran}$ space. The argument generalizes the
lattice bypass of DK-$1\frac{1}{2}$
(Theorem~\ref{thm:lattice:factorization-koszul}): in the lattice
case, $E_1 = 0$ (Heisenberg acyclicity) gave immediate degeneration;
here the $E_\infty$ page is nontrivial but finite-dimensional, which
suffices for the factorization descent.

\begin{theorem}[\texorpdfstring{$\infty$}{infinity}-categorical factorization Koszul duality
via sectorwise convergence; \ClaimStatusProvedHere]
\label{thm:h-level-factorization-kd}
\index{Koszul duality!factorization!sectorwise|textbf}
\index{sectorwise finiteness!factorization Koszul duality}
Let~$\cA$ be an $\Eone$-chiral algebra on a smooth curve~$X$
satisfying:
\begin{enumerate}[label=\textup{(H\arabic*)}]
\item\label{h1:koszulness} \emph{$\Eone$-Koszulness}: the cobar-bar
 counit
 $\Omega(\barB(\cA)) \to \cA$ is a quasi-isomorphism
 \textup{(}Theorem~B on the Koszul locus\textup{)};
\item\label{h2:sectorwise} \emph{Sectorwise finiteness}: the
 factorization bar complex $\barB^{\mathrm{fact}}(\cA)$ admits a
 $\Gamma$-grading \textup{(}for a finitely generated abelian
 group~$\Gamma$\textup{)} and a descending
 filtration~$F^\bullet$ compatible with the grading, such that
 $\operatorname{gr}^p \barB_\gamma$ is finite-dimensional
 over each $\operatorname{Ran}$-stratum;
\item\label{h3:convergence} \emph{Spectral convergence}: the
 associated spectral sequence stabilizes at each tridegree
 \textup{(}automatic by
 Theorem~\textup{\ref{thm:sectorwise-spectral-convergence}}
 when~\ref{h2:sectorwise} holds\textup{)}.
\end{enumerate}
Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The factorization bar-cobar counit
 \[
 \varepsilon^{\mathrm{fact}}\colon
 \Omega^{\mathrm{fact}}(\barB^{\mathrm{fact}}(\cA)) \to \cA
 \]
 is a quasi-isomorphism of factorization algebras on
 $\operatorname{Ran}(X)$.
\item The factorization Verdier intertwining
 $\mathbb{D}_{\mathrm{Ran}}\,
 \barB^{\mathrm{fact}}(\cA)
 \simeq (\cA^!)_\infty$
 holds at the factorization level (factorization \emph{algebra}, not coalgebra).
\item The module bar functor
 \[
 \barB_{\mathrm{mod}}^{\mathrm{fact}}\colon
 \operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\cA)
 \to
 \operatorname{CoFact}_{\Eone}^{\mathrm{gen}}
 (\cA^{!,c})^{\mathrm{op}}
 \]
 is an equivalence of stable $\infty$-categories on the
 evaluation-generated cores, with braiding reversal
 $R \mapsto R^{-1}$.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Part~(i): factorization bar-cobar.}
On the diagonal stratum $\operatorname{Ran}_1(X) \cong X$, the
factorization counit $\varepsilon^{\mathrm{fact}}$ restricts to
the ordinary cobar-bar counit
$\varepsilon\colon \Omega(\barB(\cA)) \to \cA$,
which is a quasi-isomorphism by hypothesis~\ref{h1:koszulness}
(Theorem~B).

For $n \ge 2$ and disjoint opens
$U_1, \ldots, U_k \subset X$, the factorization isomorphisms
decompose both source and target:
\begin{align*}
\Omega^{\mathrm{fact}}(\barB^{\mathrm{fact}}(\cA))
 (U_1 \sqcup \cdots \sqcup U_k)
&\cong \bigotimes_{j=1}^k
 \Omega^{\mathrm{fact}}(\barB^{\mathrm{fact}}(\cA))(U_j), \\
\cA(U_1 \sqcup \cdots \sqcup U_k)
&\cong \bigotimes_{j=1}^k \cA(U_j).
\end{align*}
The counit decomposes as $\varepsilon^{\mathrm{fact}}
= \varepsilon|_{U_1} \otimes \cdots \otimes \varepsilon|_{U_k}$,
and each factor $\varepsilon|_{U_j}$ is a quasi-isomorphism
by hypothesis~\ref{h1:koszulness} on the single-point stratum;
the K\"unneth formula for derived tensor products of chain
complexes over a field preserves quasi-isomorphisms, so the
tensor product is a quasi-isomorphism.

On arbitrary opens (including overlapping configurations), the
factorization algebra is determined by descent: a factorization
algebra on~$\operatorname{Ran}(X)$ is a cosheaf for the
factorization topology, whose basis consists of products of disjoint
opens. Sectorwise finiteness~\ref{h2:sectorwise} guarantees that
$\barB^{\mathrm{fact}}(\cA)$ is a genuine factorization coalgebra
on~$\operatorname{Ran}(X)$ (not merely a formal pro-object), so
the cosheaf condition applies. A map of factorization cosheaves
that is a quasi-isomorphism on every basis open is a global
quasi-isomorphism, giving~(i).

\emph{Part~(ii): Verdier intertwining.}
The Verdier intertwining on~$\operatorname{Ran}_1$ is
Theorem~A\textsubscript{2}
(Theorem~\ref{thm:bar-cobar-verdier}).
For disjoint opens
$U_1 \sqcup \cdots \sqcup U_k$, Verdier duality distributes as
$\mathbb{D}_{\mathrm{Ran}}
\simeq \mathbb{D}_{U_1} \boxtimes \cdots \boxtimes \mathbb{D}_{U_k}$,
so the factorization bar intertwining decomposes into a tensor
product of the $\operatorname{Ran}_1$ intertwining on each factor.
The same cosheaf descent as part~(i) extends from disjoint to
arbitrary opens.

\emph{Part~(iii): module equivalence.}
On evaluation objects, the module bar functor is an equivalence by
DK-1 (Theorem~\ref{thm:factorization-dk-eval}). The
evaluation-generated core
$\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\cA)$ is the
smallest full stable idempotent-complete braided monoidal subcategory
containing all evaluation objects. Since the module bar functor
is exact and braided monoidal with reversal
(Theorem~\ref{thm:monoidal-module-koszul}), it preserves shifts,
cones, direct summands, and ordered tensor products. Therefore, by
Proposition~\ref{prop:yangian-dk3-generated-core}, any natural
isomorphism between the identity and
$\Omega_{\mathrm{mod}} \circ \barB_{\mathrm{mod}}$ that holds on
evaluation generators extends to the full generated core.

The braiding reversal $R \mapsto R^{-1}$ is
Proposition~\ref{prop:yangian-module-koszul}(iii), extended to the
generated core by functoriality.
\end{proof}

\begin{remark}[Scope of ``unconditional'']
\label{rem:dk23-unconditional-scope}
\index{Drinfeld--Kohno!unconditional!scope}
The following corollary is ``unconditional'' in the sense that it
does not require thick generation: the sectorwise convergence
argument works for all simple types without identifying the
generated core with $D^b(\operatorname{Rep}_{\mathrm{fd}})$.
It does, however, depend on the classical Koszulness of the RTT
Yangian (Proposition~\ref{prop:yangian-koszul}), whose proof
uses Molev's PBW theorem \cite{molev-yangians} as external input.
\end{remark}

\begin{corollary}[Evaluation-generated-core DK comparison for all
simple types via sectorwise convergence; \ClaimStatusProvedHere]
\label{cor:dk23-all-types}
\index{Drinfeld--Kohno!derived!all types}
\index{sectorwise finiteness!DK for all types}
For $\fg$ any simple Lie algebra, the factorization bar-cobar
functor induces an equivalence on the evaluation-generated cores:
\begin{equation}\label{eq:dk23-all-types}
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}
 (Y_\hbar(\fg))
\;\xrightarrow{\;\sim\;}\;
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}
 (Y_{-\hbar}(\fg))^{\mathrm{op}},
\end{equation}
extending the evaluation-locus DK equivalence
\textup{(}Theorem~\textup{\ref{thm:factorization-dk-eval}}\textup{)}
to the full generated core at all types, without any
thick-generation argument.
\end{corollary}

\begin{proof}
Apply Theorem~\ref{thm:h-level-factorization-kd} to
$\cA = \mathcal{Y}(\fg)$.
Hypothesis~\ref{h1:koszulness} is
Corollary~\ref{cor:yangian-bar-cobar}: the RTT Yangian is
quadratic, pro-nilpotent, and Koszul
(Proposition~\ref{prop:yangian-koszul}), so
Theorem~\ref{thm:e1-chiral-koszul-duality} gives the
$\Eone$-chiral bar-cobar quasi-isomorphism for every
simple~$\fg$.
Hypothesis~\ref{h2:sectorwise} is
Proposition~\ref{prop:yangian-bar-loop-weight}: the $Q(\fg)$-grading
and loop filtration give the required sectorwise-finite bifiltration
for every simple~$\fg$.
Hypothesis~\ref{h3:convergence} follows from
Theorem~\ref{thm:sectorwise-spectral-convergence}.
Conclusion~(iii) gives~\eqref{eq:dk23-all-types}.
\end{proof}

\begin{remark}[H/M/S semantic levels for DK-2/3]
\label{rem:dk23-hms}
\index{Drinfeld--Kohno!H/M/S levels}
\emph{Step~A} (H-level):
Theorem~\ref{thm:h-level-factorization-kd} asserts an
equivalence of stable $\infty$-categories
$\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\cA)
\simeq
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\cA^!)^{\mathrm{op}}$
on the evaluation-generated cores, with braiding reversal
$R \mapsto R^{-1}$. This is the theorem.

\emph{Step~B} (M-level):
The proof is a dg chain-level argument: sectorwise convergence
of the bar spectral sequence on each
$\operatorname{Ran}$-stratum, extended to the full factorization
cosheaf by descent. Concretely, the module bar functor is exact
and braided monoidal
(Theorem~\ref{thm:monoidal-module-koszul}), and the
quasi-isomorphism on evaluation generators extends to the
generated core by functoriality
(Proposition~\ref{prop:yangian-dk3-generated-core}).

\emph{Reduction B$\to$A} (M-level $\to$ H-level):
The dg descent implies the $\infty$-categorical equivalence: a
map of factorization cosheaves that is a quasi-isomorphism on
every basis open is a global quasi-isomorphism in the
$\infty$-categorical sense
(Lurie~\cite[Proposition~5.5.2.2]{HA}). Thus the M-level
sectorwise quasi-isomorphisms determine the H-level equivalence
of stable $\infty$-categories.

\emph{Step~C} (S-level):
The shadow is the equality of graded dimensions
$\dim \operatorname{Ext}^i_{\cA}(V_\lambda, V_\mu)
= \dim \operatorname{Ext}^i_{\cA^!}(V_\lambda^!, V_\mu^!)$
across evaluation modules, together with the Kazhdan--Lusztig
multiplicity formula transported to the Koszul dual side.

\emph{Reduction B$\to$C} (M-level $\to$ S-level):
Taking cohomology of the M-level module bar complex
$\bar{B}_{\mathrm{mod}}(M)$ extracts the S-level Ext groups.
The sectorwise spectral sequence
(Theorem~\ref{thm:sectorwise-spectral-convergence}) converges
at each tridegree, so the M-level quasi-isomorphism on
evaluation generators yields isomorphisms of Ext groups.
\end{remark}

\begin{remark}[A proved route and a conditional route in type~\texorpdfstring{$A$}{A}; scope comparison]
\label{rem:two-dk-proofs}
\index{Drinfeld--Kohno!route comparison}
For $\fg = \mathfrak{sl}_N$, there are now two complementary routes on
the generated-core DK comparison surface
\textup{(}traditionally packaged as DK-2/3\textup{)} for the
evaluation-generated core:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Thick generation}
 \textup{(}Proposition~\ref{prop:dk2-thick-generation-typeA}\textup{)}:
 uses the
 Drinfeld polynomial classification to show that evaluation modules
 generate all finite-dimensional simples, then the composition-length
 argument of Lemma~\ref{lem:composition-thick-generation}. Theorem~\ref{conj:dk-fd-typeA}
 then records the \emph{conditional} extension criterion: once the
 ambient extension/comparison package is supplied, thick generation
 propagates the evaluation-level equivalence. This route is
 representation-theoretic and specific to type~$A$.
\item \emph{Sectorwise convergence}
 \textup{(}Corollary~\ref{cor:dk23-all-types}\textup{)}: uses
 the root lattice grading and loop filtration to bypass thick
 generation entirely. The proof is
 operadic/factorization-theoretic and works for all types.
\end{enumerate}
Route~(b) is the actual proved generated-core DK comparison on the
evaluation-generated core, and it is strictly more general
(all types $A$--$G$). Route~(a) is more explicit on type~$A$:
it identifies the module-side thick target as
$D^b(\operatorname{Rep}_{\mathrm{fd}})$ via the Drinfeld
classification and would propagate any supplied ambient
extension/comparison package beyond generators. The two routes are
compatible on type~$A$: thick generation by evaluation modules
\textup{(}Proposition~\ref{prop:dk2-thick-generation-typeA}\textup{)}
identifies the type-$A$ module-side generated core with the
evaluation-generated core already resolved by route~(b).
\end{remark}

\begin{remark}[Interaction with the four-conjecture package]
\label{rem:h-level-vs-four-conjectures}
\index{MC3!four-conjecture package!interaction with H-level}
Theorem~\ref{thm:h-level-factorization-kd} and
Corollary~\ref{cor:dk23-all-types} resolve the
evaluation-generated-core DK comparison surface
\textup{(}traditionally packaged as DK-2/3\textup{)} at all types.
The four conjectures of
Remark~\ref{rem:corrected-mc3-frontier}(b)
(Baxter exact triangles
(Conjecture~\ref{thm:baxter-exact-triangles}),
shifted-prefundamental generation
(Theorem~\ref{thm:shifted-prefundamental-generation}),
pro-Weyl recovery (Conjecture~\ref{thm:pro-weyl-recovery}), and
DK on compacts
(Conjecture~\ref{conj:dk-compacts-completion}))
concern the extension \emph{beyond} this core to
infinite-dimensional modules via a completed or coderived
enhancement.

The two projects are complementary:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The sectorwise convergence theorem gives the strongest
 factorization equivalence on the natural domain
 (evaluation-generated core) at all types.
\item The four-conjecture package enlarges the domain to include
 prefundamental and asymptotic modules, requiring new input
 (Baxter TQ-lifts, pro-Weyl limits) beyond Koszul duality.
\item The formal moduli framework below provides the categorical
 home for both projects: the evaluation-generated core is the
 compact part of the formal moduli problem, and the four-conjecture
 package extends to the completed/ind-completed part.
\end{enumerate}
\end{remark}

\subsubsection*{DK-4/5 as formal moduli Koszul duality}

The passage from DK-3 to DK-4/5, beyond the evaluation-generated
core toward the full triple bridge, gains conceptual clarity when
viewed through the lens of formal moduli problems for
$\Eone$-algebras. The abstract framework exists
unconditionally (Lurie~\cite{LurieDAGX}); once the post-core DK-3
extension/completion packet is supplied, the DK-4 task is the
identification of the tangent Lie algebra with the dg-shifted
Yangian, while the DK-5 task is the exponential/PBW passage from
the tangent Lie algebra to its formal group together with the
further comparison to the spectral quantum-group side.

\begin{definition}[Factorization formal moduli problem]
\label{def:factorization-formal-moduli}
\index{formal moduli problem!factorization|textbf}
For an $\Eone$-chiral algebra~$\cA$ on~$X$, the
\emph{factorization formal moduli problem} is the functor
\[
\mathfrak{F}_{\cA}\colon
\mathrm{CAlg}^{\mathrm{aug}}_{k}
\to \mathcal{S},
\qquad
R \;\mapsto\;
\operatorname{Map}_{\mathrm{FAlg}_{\Eone}(X)}
 \bigl(\cA \otimes R,\, \cA \otimes R\bigr)^{\simeq}
\]
from augmented commutative $k$-algebras to spaces, where the mapping
space is taken in the $\infty$-category of
$\Eone$-factorization algebras on~$\operatorname{Ran}(X)$.

By Lurie's formal moduli theorem~\cite{LurieDAGX},
$\mathfrak{F}_{\cA}$ is controlled by a dg Lie algebra
$\mathfrak{g}_{\cA} := T_{*}\mathfrak{F}_{\cA}$,
the \emph{tangent Lie algebra} of the moduli problem.
The chain-level model is classified by the bar complex:
$\mathfrak{g}_{\cA} \simeq
\operatorname{Der}(\barB^{\mathrm{fact}}(\cA))$,
the derivations of the factorization bar coalgebra.
\end{definition}

\begin{proposition}[Canonical Yangian H-level dg target from factorization
formal moduli; \ClaimStatusProvedHere]
\label{prop:yangian-canonical-hlevel-target}
For every $\Eone$-chiral algebra $\cA$ on~$X$, the factorization
formal moduli problem $\mathfrak{F}_{\cA}$ of
Definition~\ref{def:factorization-formal-moduli} has a tangent dg Lie
algebra
\[
\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA},
\]
and hence a canonically attached completed module category
\[
\operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA}).
\]
For the Yangian $\Eone$-chiral algebra
\[
\cA=\mathcal{Y}(\mathfrak{sl}_N),
\]
this gives an unconditional H-level dg target for DK-4/5.

Equivalently, the live Yangian MC4 problem is not the existence of an
H-level dg target. It is the identification of this canonical formal
moduli target with an RTT-adapted dg model whose finite quotients
recover the theorematic RTT stages and whose degree-$2$ twisting
morphism matches the ordered bar seed on the fundamental line.
\end{proposition}

\begin{proof}
Existence of the tangent dg Lie algebra $\mathfrak{g}_{\cA}$ is exactly
the content of Lurie's formal moduli theorem, as recalled in
Definition~\ref{def:factorization-formal-moduli}. The completed module
category $\operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ is
therefore canonically attached to $\cA$. Specializing to the Yangian
$\Eone$-chiral algebra gives the claimed H-level target.

The remaining sentence is a reformulation of the Yangian MC4 residual H-level identification (structural framework proved; Theorem~\ref{thm:completed-bar-cobar-strong}):
the unresolved step is to identify the canonical target
$\mathfrak{g}_{\cA}$ with an RTT-adapted dg model, not to construct the
target itself.
\end{proof}

\begin{proposition}[Canonical associative dg model of the Yangian
formal-moduli target; \ClaimStatusProvedHere]
\label{prop:yangian-canonical-envelope}
Let
\[
\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA}
\]
be the tangent dg Lie algebra of the factorization formal moduli
problem. Let
\[
U^{\mathrm{comp}}(\mathfrak{g}_{\cA})
\]
denote the completion of its universal enveloping dg algebra with
respect to the adic filtration defining complete
$\mathfrak{g}_{\cA}$-modules. Then
$U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ is a canonically attached
separated complete dg algebra, and there is a canonical equivalence
\[
\operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})
\;\simeq\;
\operatorname{Mod}^{\mathrm{comp}}\bigl(
 U^{\mathrm{comp}}(\mathfrak{g}_{\cA})
\bigr).
\]
For the Yangian $\Eone$-chiral algebra, this gives an unconditional
canonical associative dg model of the H-level target.
\end{proposition}

\begin{proof}
The universal enveloping construction extends functorially to dg Lie
algebras. Completing with respect to the same adic filtration that
defines the completed module category of the formal moduli problem
produces a separated complete dg algebra
$U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$.

By the universal property of the enveloping algebra, an action of the
dg Lie algebra $\mathfrak{g}_{\cA}$ on a complete dg module is
equivalent to an action of
$U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ on the same object, and the
intertwining morphisms are identical on both sides. Hence the
completed module categories are canonically equivalent. Specializing
to the Yangian $\Eone$-chiral algebra gives the claimed canonical
associative dg model.
\end{proof}

\begin{conjecture}[DK-4 as tangent Lie algebra identification;
\ClaimStatusConjectured]
\label{conj:dk4-formal-moduli}
\index{Drinfeld--Kohno!DK-4!formal moduli identification}
\index{dg-shifted Yangian!as tangent Lie algebra}
For the Yangian $\Eone$-chiral algebra
$\cA = \mathcal{Y}(\mathfrak{sl}_N)$:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The tangent Lie algebra
 $\mathfrak{g}_{\cA} = T_{*}\mathfrak{F}_{\cA}$
 is quasi-isomorphic, as a filtered complete dg Lie algebra, to the
 dg-shifted Yangian $\Ydg_{\cA}$ of
 Definition~\textup{\ref{def:dg-shifted-yangian}}.
\item Under this identification, the RTT-adapted filtration
 \textup{(}Definition~\textup{\ref{def:rtt-adapted-filtration}}\textup{)}
 corresponds to the canonical filtration on
 $\mathfrak{g}_{\cA}$ by order of the formal parameter: the $N$-th
 quotient $\mathfrak{g}_{\cA}/F^{N+1}$ is the tangent Lie algebra
 of the $N$-th infinitesimal neighborhood of the identity in the
 factorization group.
\item The module category equivalence
 $\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA}) \simeq
 \operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\cA)$
 is the linearization of the formal moduli problem:
 completed modules over the tangent Lie algebra classify
 infinitesimal deformations of factorization modules.
\end{enumerate}
\end{conjecture}

\begin{remark}[Relation to existing DK-4 reductions]
\label{rem:dk4-formal-moduli-vs-rtt}
\index{Drinfeld--Kohno!DK-4!formal moduli vs RTT}
Conjecture~\ref{conj:dk4-formal-moduli} provides a \emph{canonical}
construction of the dg-shifted Yangian, replacing the specific
RTT-adapted filtration of
Definition~\ref{def:rtt-adapted-filtration} with the universal
construction from formal moduli theory. The two approaches are
related:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The tangent Lie algebra $\mathfrak{g}_{\cA}$ exists
 unconditionally by Lurie's theorem; the content of
 Conjecture~\ref{conj:dk4-formal-moduli}(a) is that it has the
 specific algebraic structure of the dg-shifted Yangian.
\item The residue reductions of
 Proposition~\ref{prop:yangian-dk4-typea-frontier} are
 \emph{derived} from the formal moduli identification:
 the auxiliary-kernel identity $L_a(u) = R_{0a}(u-a)$ is
 the tangent-space computation of the moduli problem
 restricted to the fundamental evaluation line.
\item The RTT-adapted filtration of
 Definition~\ref{def:rtt-adapted-filtration} is the
 \emph{coordinate expression} of the canonical formal-moduli
 filtration in the basis provided by the RTT generators.
\end{enumerate}
This reformulation clarifies the logical structure: the RTT
identities are not independent axioms but consequences of the
universal $\infty$-categorical framework applied to the specific
$\Eone$-chiral algebra~$\mathcal{Y}(\mathfrak{sl}_N)$.
\end{remark}

\begin{conjecture}[DK-5 via \texorpdfstring{$\infty$}{infinity}-categorical PBW;
\ClaimStatusConjectured]
\label{conj:dk5-infty-pbw}
\index{Drinfeld--Kohno!DK-5!PBW argument}
\index{PBW theorem!infinity-categorical@$\infty$-categorical}
Assume Conjecture~\textup{\ref{conj:dk4-formal-moduli}(a,b)}, and
assume that the DK-3 comparison has been extended from the
evaluation-generated core to the completed factorization domain
appearing in Conjecture~\textup{\ref{conj:full-dk-bridge}}.
Then the remaining DK-5 step of the full triple bridge
\textup{(}Conjecture~\textup{\ref{conj:full-dk-bridge}}\textup{)}
reduces to a single input: the $\infty$-categorical
Poincar\'e--Birkhoff--Witt theorem for the factorization Lie
algebra~$\mathfrak{g}_{\cA}$.
\begin{enumerate}[label=\textup{(\alph*)}]
\item The formal group
 $G_{\cA} := \exp(\mathfrak{g}_{\cA})$
 is a group object in $\Eone$-factorization coalgebras on
 $\operatorname{Ran}(X)$. Its representation category
 $\operatorname{Rep}(G_{\cA})$ is a braided monoidal stable
 $\infty$-category.
\item The $\infty$-categorical PBW theorem gives an equivalence
 \[
 \operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})
 \;\simeq\;
 \operatorname{Rep}(G_{\cA})
 \]
 between completed modules over the Lie algebra and
 representations of the formal group.
\item If $G_{\cA} \simeq \QGspec(R_{\cA})$
 \textup{(}the spectral quantum group of
 Latyntsev~\cite{Latyntsev23}\textup{)}, then the remaining bridge
 equivalence in~\eqref{eq:triple-equivalence} follows from the chain
 \begin{multline*}
 \Factord(X;\cA)
 \;\xleftarrow[\textup{DK-3}]{\sim}\;
 \operatorname{CoFact}_{\Eone}(\cA^{!,c})^{\mathrm{op}}
 \\
 \;\xrightarrow[\textup{PBW}]{\sim}\;
 \operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})
 \;\xrightarrow[\exp]{\sim}\;
 \operatorname{Rep}(\QGspec(R_{\cA}))^{\mathrm{op}}.
 \end{multline*}
\end{enumerate}
\end{conjecture}

\begin{remark}[The DK ladder as successive approximation to
\texorpdfstring{$\infty$}{infinity}-categorical Koszul duality]
\label{rem:unified-dk-hierarchy}
\index{Drinfeld--Kohno!unified hierarchy}
The five DK levels are successive approximations to $\infty$-categorical Koszul duality for $\cA = \mathcal{Y}(\fg)$:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lll}
\textbf{Level} & \textbf{Content} & \textbf{Status} \\
\hline
DK-0 & Chain-level Koszul duality on $\operatorname{Ran}_1$
 & \textbf{Proved} \\
DK-1 & Extension to $\operatorname{Ran}_n$ on evaluation objects
 & \textbf{Proved} \\
DK-2/3 & Generated-core DK comparison (sectorwise convergence)
 & \textbf{Proved} \\
DK-4 & Tangent Lie algebra $=$ dg-shifted Yangian (Conjecture~\ref{conj:dk4-formal-moduli})
 & Partial (ML proved, Theorem~\ref{thm:completed-bar-cobar-strong}; algebraic identification open, Conjecture~\ref{conj:dk4-formal-moduli}) \\
DK-5 & $\infty$-PBW after post-core DK-3 extension (Conjecture~\ref{conj:dk5-infty-pbw})
 & Open \\
\end{tabular}
\end{center}
DK-0/1: Drinfeld--Kohno $+$ Kazhdan--Lusztig. DK-2/3: Boardman convergence of the loop spectral sequence (Theorem~\ref{thm:h-level-factorization-kd}). DK-4: structural framework proved (MC4 closed, Theorem~\ref{thm:completed-bar-cobar-strong}); algebraic identification open (Conjecture~\ref{conj:dk4-formal-moduli}). DK-5: once the post-core extension/completion packet beyond DK-2/3 is supplied, the remaining bridge step is the exponential/PBW passage $\mathfrak{g}_{\cA} \rightsquigarrow G_{\cA}$ together with the further identification of $G_{\cA}$ with Latyntsev's spectral quantum group~\cite{Latyntsev23}. \ifannalsedition\else Target: Conjecture~\ref{conj:master-dk-kl}.\fi

\emph{CG constraint on DK-5.}
The prefundamental Clebsch--Gordan
(Proposition~\ref{prop:prefundamental-clebsch-gordan})
constrains DK-5 as follows: since
$V_n \otimes L^- \cong \bigoplus L^-(\text{shifted})$
shows that $L^-$ is evaluation-stable, the quantum group
representation $\operatorname{Rep}(\QGspec(R_{\cA}))$ must
contain a corresponding family of objects that is closed under
tensoring with the fundamental. At the level of $q$-characters
(Frenkel--Reshetikhin), this forces the DK-5 functor to
intertwine the prefundamental TQ system
$[V_1] \cdot [L^-] = [L^-(+1)] + [L^-(-1)]$
with the QQ-system of the quantum group.
\end{remark}

\begin{proposition}[DK-5 for $\mathfrak{sl}_2$ via FRT
reconstruction; \ClaimStatusProvedHere]
\label{prop:dk5-sl2-frt}
\index{Drinfeld--Kohno!DK-5!sl2@$\mathfrak{sl}_2$ resolution|textbf}
\index{FRT construction!DK-5 resolution}
\index{quantum group!FRT reconstruction from bar complex}
For $\fg = \mathfrak{sl}_2$ at generic~$q$, the
full Hopf algebra $U_q(\mathfrak{sl}_2)$ is uniquely
determined by the Yang $R$-matrix
$R(u) = uI + \hbar P$ arising from the bar complex
$\barB^{\mathrm{ord}}(\widehat{\mathfrak{sl}}_{2,k})$
via the FRT construction.
\begin{enumerate}[label=\textup{(\roman*)}]
\item The $R$-matrix satisfies the Yang--Baxter equation and
 strong unitarity $R_{12}(u)\,R_{21}(-u) = (u^2 - \hbar^2)I$.
\item The FRT relations $R\,T_1\,T_2 = T_2\,T_1\,R$
 produce the Drinfeld--Jimbo coproduct
 $\Delta(E) = E \otimes K + I \otimes E$,
 $\Delta(F) = F \otimes I + K^{-1} \otimes F$,
 $\Delta(K) = K \otimes K$.
\item Rigidity: $H^2(U_q(\mathfrak{sl}_2), \mathbb{k}) = 0$
 ensures the reconstruction is unique
 \textup{(}no deformation ambiguity\textup{)}.
\item At roots of unity $q = e^{2\pi i/(k+2)}$, the Verlinde
 truncation at spin $j = (k{+}1)/2$ is a direct consequence:
 the quantum dimension $[k{+}2]_q = 0$ forces vanishing
 of the trace on spin-$(k{+}1)/2$ representations.
\end{enumerate}
\end{proposition}

\begin{proof}
The Yang $R$-matrix is constructed from the bar complex
via the collision residue
(Theorem~\ref{thm:factorization-dk-eval}). The FRT
procedure applied to $R(u) = uI + \hbar P$ yields
the RTT algebra; the standard Faddeev--Reshetikhin--Takhtajan
argument identifies this with $U_q(\mathfrak{sl}_2)$ at
$q = e^{i\hbar}$. Rigidity follows from the vanishing of the
second Hochschild--Kostant--Rosenberg cohomology of
$U_q(\mathfrak{sl}_2)$ at generic~$q$, which in turn follows
from the semisimplicity of the representation category.
The Verlinde truncation is immediate from the quantum
dimension formula $[n]_q = \sin(n\pi/(k{+}2))/\sin(\pi/(k{+}2))$.
\end{proof}

\begin{conjecture}[Restricted DK-5: evaluation-generated triple bridge;
\ClaimStatusConjectured]
\label{conj:restricted-dk5}%
\index{Drinfeld--Kohno!DK-5!restricted|textbf}%
\index{thick generation!restricted DK-5}%
\index{triple equivalence!evaluation-generated core}%
Let $\fg$ be a simple Lie algebra, and let
\[
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\mathcal{Y}(\fg))
\subset \operatorname{Fact}_{\Eone}(\mathcal{Y}(\fg)),
\qquad
\operatorname{Rep}_{\mathrm{fd}}^{\mathrm{gen}}(U_q(\fg))
\subset \operatorname{Rep}(U_q(\fg))
\]
be the full stable idempotent-complete braided monoidal subcategories
generated by evaluation modules
$\{V_{\omega_i}(a) : i \in \mathrm{vert}(\mathrm{Dyn}(\fg)),\;
a \in \mathbb{C}\}$. Let
${\Ydg_{\cA}}^{\mathrm{gen}}$ be the restriction of the dg-shifted
Yangian $\Ydg_{\cA}$ to the evaluation-generated sector. Then
there are equivalences of braided monoidal stable
$\infty$-categories
\begin{equation}\label{eq:restricted-dk5-triple}
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\mathcal{Y}(\fg))
\;\simeq\;
\operatorname{Mod}^{\mathrm{gen}}(\Ydg_{\cA})
\;\simeq\;
\operatorname{Rep}_{\mathrm{fd}}^{\mathrm{gen}}(U_q(\fg))^{\mathrm{op}},
\end{equation}
compatible with the DK-1 evaluation-locus equivalence
\textup{(}Theorem~\textup{\ref{thm:factorization-dk-eval}}\textup{)}
and the KZ monodromy package.
\end{conjecture}

\begin{remark}[Inputs to the restricted DK-5]
\label{rem:restricted-dk5-inputs}
Two of the three ingredients are proved unconditionally for all
simple types.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Thick generation.}
 For every simple~$\fg$, the evaluation modules
 $\{V_{\omega_i}(a)\}$ thickly generate
 $D^b(\mathrm{Rep}_{\mathrm{fd}}(Y_\hbar(\fg)))$
 \textup{(}Corollary~\textup{\ref{cor:dk2-thick-generation-all-types}}\textup{)}.
 The subcategory
 $\operatorname{Rep}_{\mathrm{fd}}^{\mathrm{gen}}(U_q(\fg))$
 therefore contains every finite-dimensional irreducible.
\item \emph{Categorical Clebsch--Gordan.}
 The all-types CG closure
 \textup{(}Theorem~\textup{\ref{thm:categorical-cg-all-types}},
 via the multiplicity-free $\ell$-weight property of
 Chari--Moura~\cite{ChariMoura06}\textup{)} ensures that
 the evaluation-generated core is closed under the tensor
 operations needed for the factorization comparison.
\item \emph{DK-2/3 on the generated core.}
 The outer equivalence on the evaluation-generated core is
 proved
 \textup{(}Corollary~\textup{\ref{cor:dk23-all-types}}\textup{)}.
 What remains is the middle term: the dg-shifted Yangian
 identification~\textup{(}DK-4 restricted to the generated
 sector\textup{)} and the PBW/exponential
 passage~\textup{(}DK-5 on the generated core\textup{)}.
\end{enumerate}
The full DK-5 \textup{(}Conjecture~\textup{\ref{conj:dk5-infty-pbw}}\textup{)}
requires extending beyond the evaluation-generated core to the full
module category~$\mathcal{O}$. The restricted conjecture avoids
this extension entirely: the thick subcategory generated by
evaluation modules is the natural domain on which all proved inputs
\textup{(}MC3, thick generation, DK-2/3\textup{)} converge.
\end{remark}

\begin{remark}[The RTT relation as Koszul duality datum]
\label{rem:rtt-is-the-duality-datum}
\index{Yangian!RTT as Koszul datum}
\index{Koszul duality!engine of DK ladder}
The common algebraic datum behind the proved DK ladder
\textup{(}DK-0 through DK-3 on the evaluation-generated core,
unconditional at all simple types\textup{)} is the RTT presentation.
But the proof is not a one-idea argument: quadratic duality,
PBW/Koszulness, and sectorwise spectral descent enter as
logically distinct inputs organized around that datum.
\smallskip
\begin{center}
\emph{The RTT relation
$R_{12}(u\!-\!v)\,T_1(u)\,T_2(v)
= T_2(v)\,T_1(u)\,R_{12}(u\!-\!v)$
is simultaneously the defining relation of the algebra
and the input to Koszul duality.}
\end{center}

\smallskip\noindent
Three consequences organize the proved surface:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Quadratic $\Rightarrow$ $R$-matrix inversion.}
 The RTT relation is quadratic in~$T$; the orthogonal complement
 $R^\perp$ of the $R(u)$-relations is the $R^{-1}(u)$-relations,
 so $Y(\fg)^! = Y_{-\hbar}(\fg)$
 (Theorem~\ref{thm:yangian-koszul-dual}).

\item \emph{PBW $\Rightarrow$ Koszulness.}
 Molev's PBW basis gives a flat deformation to
 $\operatorname{Sym}(V)$; $\operatorname{Sym}$ is classically
 Koszul; flatness transfers Koszulness to~$Y(\fg)$, giving
 bar-cobar recovery for free
 (Proposition~\ref{prop:yangian-koszul},
 Corollary~\ref{cor:yangian-bar-cobar}).

\item \emph{Root grading $\Rightarrow$ sectorwise convergence.}
 The root lattice $Q(\fg)$ decomposes the bar complex into sectors
 with $\dim V_r = (\dim V_0)^2$ uniformly; a non-increasing
 sequence of non-negative integers stabilizes; the factorization
 bar complex is therefore a genuine coalgebra on
 $\operatorname{Ran}(X)$, and K\"unneth $+$ cosheaf descent extend
 the diagonal quasi-isomorphism to all strata
 (Theorem~\ref{thm:sectorwise-spectral-convergence},
 Theorem~\ref{thm:h-level-factorization-kd}).
\end{enumerate}
These are logically independent inputs. Items~\textup{(a)} and
\textup{(b)} control the algebraic Koszul-dual surface, while
\textup{(c)} is the separate sectorwise-convergence/descent step
that upgrades the diagonal quasi-isomorphism to DK-2/3 for every
simple~$\fg$ without any thick-generation argument.

The deeper unity is organizational rather than eliminative:
\emph{the RTT presentation supplies the common algebraic source},
while PBW shows that the quadratic extraction is faithful and the
root grading makes the factorization descent converge. In that
sense, all three are built around
\emph{the RTT presentation expressing the Yangian as a quadratic
algebra whose defining relations encode the $R$-matrix}.
The bar construction extracts the $R$-matrix and inverts it;
PBW guarantees this extraction is lossless; the root grading
guarantees it converges sector by sector. Geometrically:
bar-cobar duality is Verdier duality on ordered configuration
spaces, and Verdier duality reverses the orientation of ordered
collisions, which inverts the $R$-matrix. The RTT presentation
is, in this precise sense, the Yangian \emph{presenting itself as
a Koszul duality problem}.

For the conjectural levels, the same RTT/PBW/root-grading package
continues to organize the \emph{bar-side} completion story, but it
does not by itself close DK-4 or DK-5.
It gives surjective
transition maps $\bigwedge^n(V_{\leq N+1}^*) \twoheadrightarrow
\bigwedge^n(V_{\leq N}^*)$ on the associated graded of bar
cohomology, hence Mittag-Leffler for the RTT tower
(Theorem~\ref{thm:rtt-mittag-leffler}) and a well-behaved
completed bar-cobar equivalence
(Corollary~\ref{cor:completed-bar-cobar-yangian}).
What remains at DK-4 is the separate structure identification:
$\varprojlim_N \fg_N \cong \Ydg_\cA$
(Maurer--Cartan element, translation, coproduct).
Downstream, DK-5 still sits beyond the post-core DK-3
extension/completion packet and then requires the
$\infty$-categorical PBW exponential
$\operatorname{Mod}(\fg_\cA) \simeq
\operatorname{Rep}(\exp(\fg_\cA))$.
\end{remark}

\subsubsection*{Coderived factorization duality off the Koszul locus}

On the Koszul locus (generic levels, evaluation-generated core),
Theorem~\ref{thm:h-level-factorization-kd} provides an equivalence
in the ordinary derived sense. Off the Koszul locus (at admissible
affine levels, minimal-model central charges, or for infinite-dimensional
modules beyond the generated core), the bar-cobar object persists as a
\emph{curved} factorization coalgebra, and the correct framework is the
coderived/contraderived category of
Positselski~\cite{Positselski11}.

\begin{theorem}[Factorization Positselski equivalence on the bar-coalgebra surface; \ClaimStatusProvedHere]
\label{thm:factorization-positselski}
\index{Positselski!factorization equivalence|textbf}
\index{coderived category!factorization|textbf}
\index{factorization co-contra comparison!off the Koszul locus}
Let~$\cA$ be an $\Eone$-chiral algebra on~$X$ satisfying
hypotheses~\ref{h2:sectorwise} and~\ref{h3:convergence} of
Theorem~\textup{\ref{thm:h-level-factorization-kd}}
\textup{(}sectorwise finiteness and spectral convergence\textup{)},
but not necessarily~\ref{h1:koszulness}
\textup{(}$\Eone$-Koszulness\textup{)}.
Let $C = \barB^{\mathrm{fact}}(\cA)$ denote the curved factorization
bar coalgebra. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The factorization coderived category
 $D^{\mathrm{co}}(C\text{-}\mathrm{CoFact}_{\Eone}^{\mathrm{conil}})$
 is a well-defined stable $\infty$-category: the sectorwise
 finiteness of~$C$ ensures that each $Q(\fg)$-sector is a
 genuine conilpotent coalgebra \textup{(}not a formal
 pro-object\textup{)}, so the coacyclicity localizing
 subcategory is well-defined.
 \item There is a triangulated equivalence
 \begin{equation}\label{eq:factorization-positselski}
 D^{\mathrm{co}}\bigl(
 C\text{-}\mathrm{CoFact}_{\Eone}^{\mathrm{conil}}
 \bigr)
 \;\simeq\;
 D^{\mathrm{ctr}}\bigl(
 C\text{-}\mathrm{ContraFact}_{\Eone}^{\mathrm{comp}}
 \bigr),
 \end{equation}
 where the left side is the coderived category of conilpotent
 $\Eone$-factorization comodules over~$C$, and the right side is
 the contraderived category of complete \textup{(}pro-nilpotent\textup{)}
 $\Eone$-factorization contramodules over the same curved
 factorization coalgebra~$C$.
\item On the Koszul locus \textup{(}when~\ref{h1:koszulness}
 also holds\textup{)}, the coderived and ordinary derived categories
 coincide on compact objects. Together with the separate
 factorization Verdier/bar-dual identification of
 Theorem~\textup{\ref{thm:h-level-factorization-kd}(ii)}, the
 bar-coalgebra comparison~\eqref{eq:factorization-positselski}
 is compatible with the generated-core equivalence of
 Theorem~\textup{\ref{thm:h-level-factorization-kd}(iii)}.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Part~(i).}
Sectorwise finiteness (hypothesis~\ref{h2:sectorwise}) gives
$C = \bigoplus_{\gamma} C_\gamma$ with each $C_\gamma$
finite-dimensional over each $\operatorname{Ran}$-stratum.
The factorization structure on~$C$ preserves the
$Q(\fg)$-grading (Proposition~\ref{prop:yangian-bar-loop-weight}(a)),
so the coaugmentation filtration
$F_0 C \subset F_1 C \subset \cdots$ has each
$F_n C_\gamma$ finite-dimensional. The conilpotency condition
$C = \bigcup_n F_n C$ then holds sector-by-sector, and the
coacyclicity localizing subcategory (thick closure of totalizations
of exact triples, closed under coproducts) is well-defined
by the same argument as
Definition~\ref{def:chiral-coderived}, applied sectorwise.

\emph{Part~(ii).}
The chain-level comodule-contramodule correspondence
(Theorem~\ref{thm:chiral-co-contra-correspondence}) provides the
equivalence on
$\operatorname{Ran}_1(X) \cong X$. The factorization structure
propagates this to $\operatorname{Ran}_n$ by the same
K\"unneth--descent argument as
Theorem~\ref{thm:h-level-factorization-kd}(i):
on disjoint opens the equivalence decomposes as a tensor product
of chain-level equivalences, and the factorization cosheaf
condition extends to overlapping configurations. Sectorwise
finiteness ensures the tensor products are well-defined
(no infinite-dimensionality obstructions).

\emph{Part~(iii).}
On the Koszul locus, the curvature vanishes:
$h = m_0^{(g)} = 0$ at genus~$0$
(Theorem~\ref{thm:higher-genus-inversion}(a)). When $h = 0$,
coacyclic = acyclic (Positselski~\cite[Thm~3.7]{Positselski11}),
so $D^{\mathrm{co}} = D^b$ on compact objects. The restriction
of~\eqref{eq:factorization-positselski} to compact objects therefore
lives in the ordinary derived setting. The further identification of
that compact comparison with
Theorem~\ref{thm:h-level-factorization-kd}(iii) uses the separate
Koszul-locus factorization Verdier/bar-dual statement
\textup{(}Theorem~\textup{\ref{thm:h-level-factorization-kd}(ii)}\textup{)},
which is not part of the off-Koszul Positselski proof itself.
\end{proof}

\begin{remark}[The coderived category as the natural ambient]
\label{rem:coderived-natural-ambient}
\index{coderived category!as natural ambient for DK}
The equivalence~\eqref{eq:factorization-positselski} is the
\emph{correct categorical context} for the remaining off-Koszul MC3
extension packets:
\begin{enumerate}[label=\textup{(\alph*)}]
\item On the Koszul locus (generic level), DK-0 through DK-3
 live in the ordinary derived category, and the coderived
 category adds nothing new. This is the domain of
 Theorem~\ref{thm:h-level-factorization-kd}.
\item Off the Koszul locus (admissible levels, minimal-model central
 charges), the bar-cobar object~$\Omega(C)$ is curved:
 $d^2 = h \neq 0$. Ordinary cohomological derived methods no
 longer capture the curved bar-cobar object, but the coderived
 category retains the full categorical information.
 The four conjectures of
 Remark~\ref{rem:corrected-mc3-frontier}(b)
 naturally live here: Baxter exact triangles, shifted-prefundamental
 generation, pro-Weyl recovery, and DK on compacts are all
 most naturally formulated relative to the
 coderived/contraderived bar-coalgebra setting
 of~\eqref{eq:factorization-positselski}. What
 \eqref{eq:factorization-positselski} does \emph{not} by itself
 supply is the additional module-theoretic, compact-generation,
 or formal-neighborhood input appearing in those conjectures.
\item The passage from the evaluation-generated core (compact objects
 in $D^b$) to a presentable cocompletion is controlled by the
 ind-completion of that generated core: see
 Theorem~\ref{thm:ind-completed-extension} below. Identifying this
 cocompletion with the full category~$\mathcal{O}$ requires
 additional compact-generation/comparison input and is not part of
 that theorem.
\end{enumerate}
\end{remark}

\subsubsection*{Ind-completed factorization extension}

The passage from the evaluation-generated core to its formal
presentable cocompletion is a standard categorical construction once
the compact part is established. This should not be confused with a
theorematic identification of that cocompletion with the full Yangian
category~$\mathcal{O}$.

\begin{theorem}[Ind-completion of the generated-core DK equivalence; \ClaimStatusProvedHere]
\label{thm:ind-completed-extension}
\index{ind-completion!factorization DK|textbf}
\index{Drinfeld--Kohno!ind-completed extension}
Under the hypotheses of
Theorem~\textup{\ref{thm:h-level-factorization-kd}},
the equivalence on evaluation-generated cores extends uniquely
to an exact colimit-preserving equivalence of ind-completed
categories:
\begin{equation}\label{eq:ind-completed-dk}
\operatorname{Ind}\bigl(
 \operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\cA)
\bigr)
\;\simeq\;
\operatorname{Ind}\bigl(
 \operatorname{CoFact}_{\Eone}^{\mathrm{gen}}(\cA^{!,c})
 ^{\mathrm{op}}
\bigr).
\end{equation}
In particular, both sides are presentable stable
$\infty$-categories.
\end{theorem}

\begin{proof}
The evaluation-generated core
$\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\cA)$ is a small,
idempotent-complete, stable $\infty$-category
(Proposition~\ref{prop:yangian-dk3-generated-core}). The
equivalence of Theorem~\ref{thm:h-level-factorization-kd}(iii) is
an exact functor between small stable $\infty$-categories. By
the universal property of ind-completion
(Lurie~\cite[Prop.~5.3.5.10]{HTT}), any exact equivalence between
small stable $\infty$-categories extends uniquely to a
colimit-preserving equivalence between their ind-completions.
This gives~\eqref{eq:ind-completed-dk}.

Presentability follows from $\operatorname{Ind}(\mathcal{C})$
being presentable whenever $\mathcal{C}$ is small and
idempotent-complete (Lurie~\cite[Prop.~5.5.7.8]{HTT}).
Stability is preserved by ind-completion.
\end{proof}

\begin{remark}[Ind-completion vs.\ pro-Weyl completion]
\label{rem:ind-vs-proweyl}
\index{pro-Weyl completion!vs.\ ind-completion}
The ind-completed category
$\operatorname{Ind}(\operatorname{Fact}_{\Eone}^{\mathrm{gen}})$
is the \emph{free cocompletion} of the generated core: it
formally adds all filtered colimits. This is a strictly larger
category than the generated core but a strictly smaller one than
the full coderived category
$D^{\mathrm{co}}(\barB^{\mathrm{fact}}\text{-}\mathrm{CoFact})$
of Theorem~\ref{thm:factorization-positselski}.

The four conjectures of
Remark~\ref{rem:corrected-mc3-frontier}(b) concern modules
that lie in the ind-completion but not in the generated core:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Standard modules} $M(\Psi)$: by
 Conjecture~\ref{thm:pro-weyl-recovery}, these are
 pro-Weyl limits $R\varprojlim_m W_m$, where each~$W_m$ is
 compact (evaluation-generated). The pro-object
 $\{W_m\}$ defines an object of $\operatorname{Pro}(\mathcal{C})
 \hookrightarrow \operatorname{Ind}(\mathcal{C})$
 via the canonical functor
 $\operatorname{Pro}(\mathcal{C}) \to
 \operatorname{Ind}(\mathcal{C})^{\mathrm{op}}$.
\item \emph{Prefundamental modules} $L^-_{i,a}$: by
 Theorem~\ref{thm:shifted-prefundamental-generation}, these
 are compact generators of the completed shifted category.
 In the ind-completed factorization category, $L^-_{i,a}$
 should be representable as a filtered colimit of evaluation
 objects (via the Baxter exact triangles of
 Conjecture~\ref{thm:baxter-exact-triangles}).
\end{enumerate}
The equivalence~\eqref{eq:ind-completed-dk} provides the
categorical framework in which both types of extensions live.
\end{remark}

\subsubsection*{The four conjectures in the formal moduli framework}

The formal moduli problem~$\mathfrak{F}_{\cA}$
(Definition~\ref{def:factorization-formal-moduli}) provides a
unified $\infty$-categorical formulation of the four MC3
conjectures. Each conjecture becomes a statement about the
tangent Lie algebra~$\mathfrak{g}_{\cA}$ or the formal
group~$G_{\cA} = \exp(\mathfrak{g}_{\cA})$.

\begin{conjecture}[Formal moduli reformulation of MC3;
\ClaimStatusConjectured]
\label{conj:mc3-formal-moduli-reformulation}
\index{MC3!formal moduli reformulation}
\index{formal moduli problem!MC3}
The four MC3 components (with the all-types categorical CG and
evaluation-generated-core surfaces now separated from the remaining
completion packets) admit conjectural reformulations in terms
of the factorization formal moduli problem~$\mathfrak{F}_{\cA}$
and the tangent Lie algebra
$\mathfrak{g}_{\cA} = T_{*}\mathfrak{F}_{\cA}$:
\begin{enumerate}[label=\textup{(\Roman*)}]
\item \emph{Baxter
 \textup{(}Conjecture~\textup{\ref{thm:baxter-exact-triangles}}\textup{)}
 as infinitesimal deformation exact triangles.}
 The Baxter TQ relations lift to distinguished triangles in
 the category $\operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})$
 of completed modules over the tangent Lie algebra. The
 companion module $M_{k,x}^{(i)}$ represents the tangent
 vector to the evaluation deformation at the point
 $(k, x) \in \mathbb{C}^2$, and the TQ triangle is the
 fiber sequence of the tangent map
 $T_{(k,x)}\mathfrak{F}_{\cA} \to
 T_{(k',x')}\mathfrak{F}_{\cA}$.

\item \emph{Shifted-prefundamental generation
 \textup{(}Theorem~\textup{\ref{thm:shifted-prefundamental-generation}}\textup{)}
 as compact generation of the tangent category.}
 The compact objects of
 $\operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})$
 are the thick closure of tangent representations at
 evaluation and prefundamental points. In the formal moduli
 picture, these are the tangent spaces to the evaluation
 locus (compact, by the proved DK-1) and the
 prefundamental locus (conjecturally compact).

\item \emph{Pro-Weyl recovery
 \textup{(}Conjecture~\textup{\ref{thm:pro-weyl-recovery}}\textup{)}
 as completeness of the formal moduli problem.}
 For a rational $\ell$-weight~$\Psi$, the standard module
 $M(\Psi)$ is the derived global sections of the formal
 neighborhood of~$\Psi$ in the moduli of $\ell$-weights:
 \[
 M(\Psi)
 \;\simeq\;
 R\Gamma\bigl(\widehat{\mathrm{Spec}\,
 \mathcal{O}}_\Psi,\;
 \mathcal{V}_{\mathfrak{F}_{\cA}}\bigr)
 \;\simeq\;
 R\varprojlim_m\, W_m,
 \]
 where the Weyl modules~$W_m$ are the values of the moduli
 functor on the $m$-th infinitesimal neighborhood.

\item \emph{DK on compacts
 \textup{(}Conjecture~\textup{\ref{conj:dk-compacts-completion}}\textup{)}
 as formal GAGA.}
 The bar-cobar equivalence extends from the generic
 fiber (evaluation locus) to the formal neighborhood
 (completed category) by a formal GAGA principle for
 the factorization formal moduli problem:
 coherent sheaves on the formal completion agree with
 algebraic coherent sheaves on the Koszul locus.
\end{enumerate}
\end{conjecture}

\begin{remark}[Tangent Lie algebra controls the extension package]
\label{rem:tangent-controls-extension}
\index{tangent Lie algebra!role in MC3 extension}
The formal moduli reformulation
(Conjecture~\ref{conj:mc3-formal-moduli-reformulation})
reveals the organizing role of the tangent Lie
algebra~$\mathfrak{g}_{\cA}$: the remaining extension
conjectures beyond the proved MC3 evaluation-generated core can be organized over a common structural background,
namely that $\mathfrak{g}_{\cA}$ is \emph{algebraizable}:
that the formal moduli problem~$\mathfrak{F}_{\cA}$ is the
formal completion of a global (algebraic) moduli problem.

In the DK-4 framework
(Conjecture~\ref{conj:dk4-formal-moduli}), algebraizability is the
content of the RTT-adapted filtration: the formal
group~$G_{\cA}$ admits a filtration whose finite quotients are
the finite RTT stages, and the transition maps are the RTT
truncations. If this filtration is Mittag-Leffler on cohomology
(the concrete form of algebraizability), the strong
completion-tower theorem
\textup{(}Theorem~\ref{thm:completed-bar-cobar-strong}\textup{)}
supplies the bar-side completed Koszul framework relevant to the
remaining MC3 packets. What it does \emph{not} by itself prove is
the module-theoretic content of Baxter exact triangles,
shifted-prefundamental generation, pro-Weyl recovery, or DK on
compacts; those still require additional identifications on the
appropriate completed module/formal-neighborhood surfaces.

This suggests a staged alternative route: first establish the
Mittag--Leffler/completion framework on the RTT tower, then
separately identify how each remaining MC3 packet is encoded in
that common formal-moduli setting.
\end{remark}

\subsubsection*{Factorization DK-4: tangent Lie algebra via
bar derivations}

Conjecture~\ref{conj:dk4-formal-moduli} identifies DK-4 with the
tangent Lie algebra computation
$\mathfrak{g}_{\cA} \simeq \Ydg_{\cA}$.
The following proposition provides the first constructive step:
the tangent Lie algebra at finite RTT stage is computable,
and the compatibility of these finite computations is the
content of DK-4.

\begin{proposition}[Finite-stage tangent Lie algebras;
\ClaimStatusProvedHere]
\label{prop:finite-stage-tangent}
\index{tangent Lie algebra!finite RTT stage}
\index{dg-shifted Yangian!finite-stage construction}
For the Yangian $\Eone$-chiral algebra
$\cA = \mathcal{Y}(\fg)$ and the $N$-th RTT truncation
$\cA_{\leq N}$, the tangent Lie algebra
$\mathfrak{g}_N := T_{*}\mathfrak{F}_{\cA_{\leq N}}$
satisfies:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $\mathfrak{g}_N$ is a finite-dimensional dg Lie algebra
 with $N \cdot (\dim V_0)^2$ generators in degree~$0$
 \textup{(}one copy of $\operatorname{End}(V_0)$ per RTT
 level; for the reduced Yangian, $N \cdot \dim \fg$
 generators\textup{)}.
\item The differential on~$\mathfrak{g}_N$ is the derivation
 of $\barB(\cA_{\leq N})$ induced by the bar differential:
 \[
 \mathfrak{g}_N
 \;\cong\;
 \operatorname{Der}^{\mathrm{cont}}\bigl(
 \barB(\cA_{\leq N}),\, \barB(\cA_{\leq N})
 \bigr)[1].
 \]
\item The truncation maps $\cA_{\leq N+1} \to \cA_{\leq N}$
 induce surjective dg Lie algebra maps
 $\mathfrak{g}_{N+1} \twoheadrightarrow \mathfrak{g}_N$,
 compatible with the bar construction.
\item At $N = 1$, $\mathfrak{g}_1 \cong \mathfrak{gl}(V_0)$
 \textup{(}the RTT generators $T_{ij}^{(0)}$ at level~$0$ span
 $\operatorname{End}(V_0)$ with the commutator bracket\textup{)},
 concentrated in degree~$0$. For the reduced Yangian
 $Y(\fg)$ \textup{(}quantum determinant quotient\textup{)},
 $\mathfrak{g}_1 \cong \fg$.
\end{enumerate}
\end{proposition}

\begin{proof}
Part~(a):
$\cA_{\leq N}$ is the quotient of~$\cA$ by generators of
level $> N$. Each level contributes $(\dim V_0)^2$
generators (the RTT modes $T_{ij}^{(r)}$ for
$0 \leq r \leq N-1$), so $\mathfrak{g}_N$ has
$N \cdot (\dim V_0)^2$ generators in degree~$0$.
Since $\cA_{\leq N}$ is quadratic and Koszul
(Proposition~\ref{prop:yangian-koszul}), the tangent Lie
algebra $\mathfrak{g}_N \cong
\operatorname{Ext}^*_{\cA_{\leq N}}(\bC, \bC)[1]$ is
finite-dimensional (each degree of the Koszul dual
$\cA_{\leq N}^!$ is finite-dimensional by local finiteness).

Part~(b):
By Lurie's formal moduli theorem~\cite{LurieDAGX}, the tangent
Lie algebra is computed as the shifted derivations of the bar
coalgebra. For the finite-dimensional quotient~$\cA_{\leq N}$,
the bar coalgebra $\barB(\cA_{\leq N})$ is finite-dimensional
(bounded bar degree by the quadratic relations), so
the derivation complex is finite-dimensional.

Part~(c):
The truncation map $\cA_{\leq N+1} \twoheadrightarrow \cA_{\leq N}$
induces a surjection
$\barB(\cA_{\leq N+1}) \twoheadrightarrow \barB(\cA_{\leq N})$
of bar coalgebras (bar is covariant on algebra maps).

For the tangent Lie algebras, the map
$\mathfrak{g}_{N+1} \to \mathfrak{g}_N$ is surjective by the
following Koszul dual argument: since $\cA_{\leq N}$ is Koszul,
the tangent Lie algebra in degree~$p$ is
$(\mathfrak{g}_N)_p \cong (\cA_{\leq N}^!)_{p+1}$.

The Koszul dual $\cA_{\leq N}^!$ has generators
$V_{\leq N}^*$ and relations $R_{\leq N}^\perp$.
Any element $f \in (\cA_{\leq N}^!)_n
\subset (V_{\leq N}^*)^{\otimes n} \cap (R_{\leq N}^\perp)_n$
extends by zero on the $V_N^*$-components to an element
$\tilde{f} \in (\cA_{\leq N+1}^!)_n$
(since $\tilde{f}$ automatically annihilates all
relations involving level-$N$ generators).
Hence $(\cA_{\leq N+1}^!)_n \twoheadrightarrow (\cA_{\leq N}^!)_n$
is surjective in every degree.

The identification
$(\mathfrak{g}_N)_p \cong (\cA_{\leq N}^!)_{p+1}$ is natural
in~$N$: it arises from Lurie's formal moduli theorem (Part~(b))
applied to each truncation, and the truncation-compatible maps of
bar coalgebras induce compatible maps on derivation complexes.
Thus the surjectivity of $(\cA_{\leq N+1}^!)_n \twoheadrightarrow
(\cA_{\leq N}^!)_n$ directly yields
$\mathfrak{g}_{N+1} \twoheadrightarrow \mathfrak{g}_N$ in every
internal degree.

Part~(d):
At $N = 1$, $\cA_{\leq 1} \cong U(\mathfrak{gl}(V_0))$ (the
$T_{ij}^{(0)}$ for $1 \leq i,j \leq \dim V_0$ generate
$\operatorname{End}(V_0) = \mathfrak{gl}(V_0)$ under the
commutator, and the RTT relation at level~$0$ reproduces the
$\mathfrak{gl}(V_0)$ bracket). The bar complex
$\barB(U(\mathfrak{gl}(V_0)))$ is the Chevalley--Eilenberg complex,
and $\operatorname{Der}(\barB(U(\mathfrak{gl}(V_0))))[1]
\cong \mathfrak{gl}(V_0)$, concentrated in degree~$0$.
The quantum determinant condition at level~$0$ reduces the
identity component, giving $\mathfrak{g}_1 \cong \fg$ for
the reduced Yangian.
\end{proof}

\begin{theorem}[Mittag-Leffler for the RTT bar cohomology tower;
\ClaimStatusProvedHere]
\label{thm:rtt-mittag-leffler}
\index{Mittag-Leffler condition!RTT tower|textbf}
\index{bar complex!RTT tower!Mittag-Leffler}
\index{Drinfeld--Kohno!DK-4!Mittag-Leffler}
For any simple Lie algebra~$\fg$, the transition maps on bar
cohomology in the RTT tower are surjective:
\[
H^n\bigl(\barB(\cA_{\leq N+1})\bigr)
\;\twoheadrightarrow\;
H^n\bigl(\barB(\cA_{\leq N})\bigr)
\qquad \text{for all } N \geq 1, \;\text{all } n \geq 0.
\]
In particular, the Mittag-Leffler condition holds and
$\varprojlim^1_N H^n(\barB(\cA_{\leq N})) = 0$.
\end{theorem}

\begin{proof}
\emph{Step~1: PBW filtration on truncated bar complexes.}
Each truncation $\cA_{\leq N} = Y(\fg)_{\leq N}$ inherits the
PBW filtration of Proposition~\ref{prop:yangian-koszul}:
$F_p \cA_{\leq N}$ is spanned by ordered monomials of total
level $\leq p$ in the RTT generators $\{T_{ij}^{(r)}\}_{r < N}$.
The associated graded is the polynomial algebra:
\[
\operatorname{gr}_F \cA_{\leq N}
\;\cong\;
\operatorname{Sym}(V_{\leq N}),
\qquad
V_{\leq N} = \bigoplus_{r=0}^{N-1}
\operatorname{End}(\bC^{N_0})_r,
\]
where $N_0 = \dim V_0$. The truncation maps
$\cA_{\leq N+1} \twoheadrightarrow \cA_{\leq N}$ preserve the
PBW filtration and induce the projection
$\operatorname{Sym}(V_{\leq N+1}) \twoheadrightarrow
\operatorname{Sym}(V_{\leq N})$ on associated graded.

\emph{Step~2: PBW spectral sequence for bar cohomology.}
The PBW filtration induces a bounded-below, exhaustive filtration
on $\barB(\cA_{\leq N})$. By
Theorem~\ref{thm:pbw-koszulness-criterion} (``bar construction
commutes with taking associated graded for flat filtrations''),
the associated spectral sequence has $E_1$ page
\[
E_1^{p,q}(\cA_{\leq N})
= H^{p+q}\bigl(\barB(\operatorname{Sym}(V_{\leq N}))\bigr).
\]
By Koszulness of $\cA_{\leq N}$
(Proposition~\ref{prop:yangian-koszul} applies to each truncation:
$\cA_{\leq N}$ is a quadratic algebra in finitely many generators
$\{T_{ij}^{(r)}\}_{r < N}$ with the restricted RTT relations, inherits
the PBW basis of Molev, and satisfies local finiteness a~fortiori),
the spectral sequence \emph{degenerates at $E_1$}:
$E_1 = E_\infty$. Indeed, Koszulness forces bar cohomology
onto the diagonal $p + q = n$, $p = n$ (homological = internal
degree), so all higher differentials $d_r$ for $r \geq 2$ have
zero source or target for bidegree reasons.

\emph{Step~3: Surjectivity on $E_1$.}
For the commutative algebra $\operatorname{Sym}(V_{\leq N})$,
the Koszul dual is $\bigwedge(V_{\leq N}^*)$, and bar cohomology
in degree~$n$ is $\bigwedge^n(V_{\leq N}^*)$. The truncation
$\operatorname{Sym}(V_{\leq N+1}) \twoheadrightarrow
\operatorname{Sym}(V_{\leq N})$ induces on bar cohomology the
projection
\[
\textstyle
\bigwedge\nolimits^n(V_{\leq N+1}^*)
\;\twoheadrightarrow\;
\bigwedge\nolimits^n(V_{\leq N}^*),
\]
which kills exactly the wedge products involving the factor
$\operatorname{End}(\bC^{N_0})_N^*$. This map is surjective
for all $N$ and $n$.

\emph{Step~4: Filtered surjectivity implies surjectivity.}
The truncation maps $\cA_{\leq N+1} \to \cA_{\leq N}$ are
compatible with the PBW filtrations, hence induce a map of
spectral sequences. On the $E_1 = E_\infty$ page, this map
is the surjection of Step~3. Since the PBW filtration on
$H^n(\barB(\cA_{\leq N}))$ is exhaustive and bounded below
(each bar degree and level contributes finitely), a standard
filtered-surjectivity argument gives: a filtered map
$f\colon M' \to M$ of filtered objects inducing a surjection
$\operatorname{gr}_p f$ on each graded piece is itself
surjective. (Proof: by induction on $p$, the image of
$f$ contains $F_p M$ for each~$p$; exhaustivity gives
$\operatorname{im}(f) = M$.)

Therefore $H^n(\barB(\cA_{\leq N+1}))
\twoheadrightarrow H^n(\barB(\cA_{\leq N}))$
is surjective for all $N$ and~$n$. Surjective transition maps
trivially satisfy Mittag-Leffler, giving
$\varprojlim^1 = 0$.
\end{proof}

\begin{corollary}[Completed bar-cobar equivalence for Yangians;
\ClaimStatusProvedHere]
\label{cor:completed-bar-cobar-yangian}
\index{bar-cobar duality!completed Yangian|textbf}
\index{Yangian!completed bar-cobar}
For any simple~$\fg$, the completed reduced bar construction
\[
\widehat{\barB}\bigl(Y(\fg)\bigr)
\;:=\;
\varprojlim_N\, \barB\bigl(Y(\fg)_{\leq N}\bigr)
\]
exists as a separated complete conilpotent $\Eone$-chiral coalgebra,
and the completed cobar-bar counit is a quasi-isomorphism:
\[
\Omega^{\mathrm{ch}}\bigl(
 \widehat{\barB}(Y(\fg))
\bigr)
\;\xrightarrow{\;\sim\;}\;
Y(\fg).
\]
This verifies
Theorem~\textup{\ref{thm:completed-bar-cobar-strong}}
for the Yangian RTT tower.
\end{corollary}

\begin{proof}
The strong completion-tower axioms of
Theorem~\ref{thm:completed-bar-cobar-strong} are verified:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Each truncation $\cA_{\leq N}$ is finite type and lies in
 the proved bar-cobar regime
 (Corollary~\ref{cor:yangian-bar-cobar}).
\item The transition maps $\cA_{\leq N+1} \to \cA_{\leq N}$ are
 compatible with the finite-stage bar constructions
 (PBW filtration compatibility,
 Proposition~\ref{prop:finite-stage-tangent}(c)).
\item The inverse system on bar complexes satisfies Mittag-Leffler
 (Theorem~\ref{thm:rtt-mittag-leffler}): the transition maps
 on bar cohomology are surjective, so
 $\varprojlim^1_N H^n(\barB(\cA_{\leq N})) = 0$.
\end{enumerate}
The Mittag-Leffler condition gives
$H^n(\widehat{\barB}(Y(\fg)))
\cong \varprojlim_N H^n(\barB(\cA_{\leq N}))$
(no $\varprojlim^1$ correction). The completed cobar differential
is continuous by
Proposition~\ref{prop:inverse-limit-differential-continuity}
(automatic for inverse systems of finite-stage curved dg
coalgebras). By the MC4 reduction principle
(Proposition~\ref{prop:mc4-reduction-principle},
now verified for this tower), the completed cobar-bar counit
restricts at each finite stage to the proved
quasi-isomorphism
$\Omega(\barB(\cA_{\leq N})) \xrightarrow{\sim} \cA_{\leq N}$,
and the Mittag-Leffler condition ensures the inverse limit
of quasi-isomorphisms is a quasi-isomorphism.
\end{proof}

\begin{conjecture}[DK-4: tangent Lie algebra identification;
\ClaimStatusConjectured]
\label{conj:dk4-inverse-limit}
\index{Drinfeld--Kohno!DK-4!inverse limit construction}
\index{tangent Lie algebra!inverse limit}
By Theorem~\textup{\ref{thm:rtt-mittag-leffler}}, the
inverse system $\{\mathfrak{g}_N\}_{N \geq 1}$ of
Proposition~\textup{\ref{prop:finite-stage-tangent}} satisfies
Mittag-Leffler with surjective transition maps, and the tangent
Lie algebra of the factorization formal moduli problem is
\[
\mathfrak{g}_{\cA}
\;=\;
T_{*}\mathfrak{F}_{\cA}
\;\cong\;
\varprojlim_N\, \mathfrak{g}_N.
\]
The remaining content of DK-4 is the identification of this
inverse limit with the dg-shifted Yangian:
\[
\varprojlim_N\, \mathfrak{g}_N
\;\cong\;
\Ydg_{\cA}.
\]
This identification is equivalent to showing that the derivation
complex $\operatorname{Der}(\widehat{\barB}(Y(\fg)))$
carries the dg-shifted RTT structure
\textup{(}Definition~\textup{\ref{def:dg-shifted-yangian}}\textup{)}:
the Maurer--Cartan element $r(z) = \tau|_{\deg 2}$, the
translation operator, and the twisted coproduct.
\end{conjecture}

\begin{remark}[DK-4 reduced to structure identification]
\label{rem:dk4-mittag-leffler}
\index{Mittag-Leffler condition!DK-4 reduction}
Theorem~\ref{thm:rtt-mittag-leffler} and
Corollary~\ref{cor:completed-bar-cobar-yangian} resolve the
\emph{analytic} part of DK-4: the inverse limit exists, is
well-behaved ($\varprojlim^1 = 0$), and the completed bar-cobar
equivalence holds. What remains is the \emph{algebraic}
identification of $\varprojlim_N \mathfrak{g}_N$ with the
dg-shifted Yangian; specifically, the three structural
data:
\begin{enumerate}[label=\textup{(\alph*)}]
\item the Maurer--Cartan element $r(z)$ arises as the
 degree-$2$ part of the bar propagator~$\tau$;
\item the translation operator is the derivation induced by
 $T_{ij}^{(r)} \mapsto T_{ij}^{(r+1)}$;
\item the twisted coproduct on $\widehat{\barB}(Y(\fg))$
 decomposes as the Drinfeld coproduct on~$\Ydg$.
\end{enumerate}
Proposition~\ref{prop:yangian-dk4-typea-frontier} isolates the
finite-stage local shadow of~(a): on the standard type-$A$ tower,
the degree-$2$ packet is reduced to the auxiliary-kernel identity
$L_a(u) = R_{0a}(u - a)$ and its residue/mixed-tensor descendants,
which form the tangent-space computation of the moduli problem
restricted to the fundamental evaluation line
(Remark~\ref{rem:dk4-formal-moduli-vs-rtt}(ii)).

The completed bar-cobar equivalence
\textup{(}Corollary~\ref{cor:completed-bar-cobar-yangian}\textup{)}
also clarifies the bar-side setting for the remaining MC3 extension
conjectures
(Conjecture~\ref{conj:mc3-formal-moduli-reformulation}):
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Pro-Weyl recovery}
 \textup{(}Conjecture~\ref{thm:pro-weyl-recovery}\textup{)}:
 on the theorematic type-$A$ surface of
 Theorem~\ref{thm:pro-weyl-recovery}, the Weyl truncation tower
 $\{W_m\}$ can be viewed inside the completed bar/factorization
 setting supplied by Corollary~\ref{cor:completed-bar-cobar-yangian}.
 What the completed bar-cobar theorem does \emph{not} by itself prove
 is the existence of that pro-Weyl tower, the surjectivity/Mittag--Leffler
 statements, or the inverse-limit identification
 $M(\Psi) \simeq R\varprojlim_m W_m$ outside the separately proved
 type-$A$ lane.

\item \emph{DK on compacts}
 \textup{(}Conjecture~\ref{conj:dk-compacts-completion}\textup{)}:
 Theorem~\ref{thm:ind-completed-extension} gives the formal
 ind-completion of the evaluation-generated core. Comparing the
 Francis--Gaitsgory pro-nilpotent completion to that cocompletion,
 and then extending the completed bar-cobar equivalence across the
 desired compact generators, is additional input. What remains is
 the compact shifted-prefundamental generation input together with
 the extra compact-core extension/completion comparison package;
 even on the type-$A$ surface, these steps are not consequences of
 Corollary~\ref{cor:completed-bar-cobar-yangian} alone.
\end{enumerate}
\end{remark}

\begin{definition}[Ordered \texorpdfstring{$\Eone$}{E1}-factorization category]
\label{def:ordered-e1-factorization}
\index{factorization category!ordered $\Eone$-|textbf}
For an $\Eone$-chiral algebra~$\cA$ on a curve~$X$,
the \emph{ordered $\Eone$-factorization category}
$\Factord(X;\cA)$ is the stable $\infty$-category
of $\cA$-modules on ordered configuration spaces,
with the associative chiral tensor structure induced
by the $\Eone$-operad action
(Definition~\ref{def:e1-factorization-category}).
\ifannalsedition\else
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\fi
\end{definition}

\begin{definition}[Spectral quantum group]
\label{def:spectral-quantum-group}
\index{quantum group!spectral|textbf}
For a Koszul dual~$\cA^!$ with spectral $R$-matrix~$R_{\cA}$,
the \emph{spectral quantum group} $\QGspec(R_{\cA})$ is the
factorization quantum group whose representation category
is controlled by the spectral $R$-matrix, in the sense of
Latyntsev~\cite{Latyntsev23}.
\ifannalsedition\else
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\fi
\end{definition}

\begin{definition}[dg-shifted Yangian]
\label{def:dg-shifted-yangian}
\index{Yangian!dg-shifted|textbf}
For a Koszul dual~$\cA^!$, the \emph{dg-shifted Yangian}
$\Ydg_{\cA}$ is the dg algebra with translation operator,
Maurer--Cartan element~$r(z)$, and twisted coproduct,
as constructed in the perturbative holomorphic-topological
setting of Costello--Yamazaki~\cite{costello-yamazaki} and
Costello--Gwilliam~\cite{CG17}.
\ifannalsedition\else
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\fi
\end{definition}

\begin{definition}[RTT-adapted filtration on a dg-shifted Yangian]
\label{def:rtt-adapted-filtration}
Let $\Ydg_{\cA}$ be a dg-shifted Yangian. An
\emph{RTT-adapted filtration} on $\Ydg_{\cA}$ is a descending
filtration by closed dg ideals
\[
F^1\Ydg_{\cA} \supset F^2\Ydg_{\cA} \supset \cdots
\]
such that:
\begin{enumerate}
\item $\Ydg_{\cA} \cong
 \varprojlim_N \Ydg_{\cA}/F^{N+1}\Ydg_{\cA}$ as a complete dg algebra;
\item the differential, translation operator, Maurer--Cartan element
 $r(z)$, and twisted coproduct preserve the filtration;
\item each quotient
 $\Ydg_{\cA}/F^{N+1}\Ydg_{\cA}$ is dg quasi-isomorphic to the finite
 RTT stage $Y_{\le N}$; and
\item these quotient quasi-isomorphisms are compatible with the RTT
 truncation maps and the finite-stage bar-cobar data.
\end{enumerate}
This is the exact H-level input required by
Corollary~\ref{cor:yangian-hlevel-comparison-criterion}.
\end{definition}

\begin{proposition}[Formal quotient criterion for dg-shifted Yangians;
\ClaimStatusProvedHere]
\label{prop:dg-shifted-quotient-criterion}
Let $\Ydg_{\cA}$ be a dg algebra equipped with:
\begin{enumerate}
\item a translation operator;
\item a Maurer--Cartan element $r(z)$;
\item a twisted coproduct; and
\item a descending sequence of closed dg ideals
 \[
 F^1\Ydg_{\cA} \supset F^2\Ydg_{\cA} \supset \cdots
 \]
 preserved by the differential, translation operator,
 Maurer--Cartan element, and twisted coproduct.
\end{enumerate}
Then every finite quotient
\[
\Ydg_{\cA}/F^{N+1}\Ydg_{\cA}
\]
inherits the same dg-shifted Yangian type of structure, and the quotient
maps form an inverse system of dg-shifted objects.

If, in addition, these quotients are dg quasi-isomorphic to the finite
RTT stages $Y_{\le N}$ compatibly with RTT truncation, evaluation
modules, and the degree-$2$ twisting morphism, then
Definition~\ref{def:rtt-adapted-filtration} holds and
Corollary~\ref{cor:yangian-hlevel-comparison-criterion} applies.
\end{proposition}

\begin{proof}
Preservation of the ideals by the differential descends the dg
structure to each quotient. Preservation by the translation operator,
Maurer--Cartan element, and twisted coproduct descends those data as
well, because each operation factors through the quotient by the same
ideal. Compatibility of the quotient maps with the preserved
operations makes the family of quotients an inverse system of
dg-shifted objects.

The additional compatibility hypotheses are exactly the remaining items
of Definition~\ref{def:rtt-adapted-filtration}. Once they are checked,
Corollary~\ref{cor:yangian-hlevel-comparison-criterion} gives the
comparison with $\widehat Y_{\mathrm{RTT}}$.
\end{proof}

\begin{conjecture}[Full derived Drinfeld--Kohno bridge;
\ClaimStatusConjectured]
\label{conj:full-dk-bridge}
\index{Drinfeld--Kohno!full bridge|textbf}
\index{triple equivalence!factorization--Yangian--quantum group}
For affine/Yangian-type modular Koszul $\Eone$-objects~$\cA$
satisfying:
\textup{(i)}~$\Eone$-Koszulness,
\textup{(ii)}~pro-nilpotent completion/convergence,
\textup{(iii)}~existence of spectral $R$-matrix data, and
\textup{(iv)}~extension of the evaluation-locus comparison to
the full category~$\mathcal{O}$,
there are equivalences of braided monoidal stable
$\infty$-categories
\begin{equation}\label{eq:triple-equivalence}
\Factord(X;\cA)
\;\simeq\;
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\;\simeq\;
\operatorname{Rep}^{\mathrm{spec}}\!
 \bigl(\QGspec(R_{\cA})\bigr)^{\mathrm{op}},
\end{equation}
compatible with evaluation modules and the KZ monodromy package on the
evaluation locus.

\smallskip\noindent
\emph{Status.}
Conjecture~\textup{\ref{conj:full-derived-dk}} is the DK-3 outer
factorization equivalence; Theorem~\textup{\ref{thm:factorization-dk-eval}}
proves DK-1 on the evaluation locus. The Yangian middle term and the
triple formulation are the DK-4/DK-5 completion.
\ifannalsedition\else
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\fi
\end{conjecture}

\begin{proposition}[Formal reduction principle from DK-3 to
DK-4/DK-5; \ClaimStatusProvedHere]
\label{prop:yangian-dk-mc4-reduction}
Fix an affine/Yangian-type modular Koszul $\Eone$-object~$\cA$.
Assume the DK-3 outer equivalence is established on the ordered
factorization model, namely that there is a braided monoidal
equivalence
\[
\Factord(X;\cA)
\xrightarrow{\sim}
\operatorname{Rep}^{\mathrm{spec}}\!
 \bigl(\QGspec(R_{\cA})\bigr)^{\mathrm{op}}
\]
compatible with evaluation modules and extending the
evaluation-locus comparison of
Theorem~\ref{thm:factorization-dk-eval}. Then the remaining task in
passing from this outer factorization comparison to a completed
H-level bridge is exactly the construction of a dg-shifted
Yangian~$\Ydg_{\cA}$ whose RTT-adapted filtration satisfies
Corollary~\ref{cor:yangian-hlevel-comparison-criterion}, together with
the module-category enhancement
\[
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\xrightarrow{\sim}
\operatorname{Rep}^{\mathrm{spec}}\!
 \bigl(\QGspec(R_{\cA})\bigr)^{\mathrm{op}}.
\]
In particular, once DK-3 is in hand, the genuinely new Yangian input is
the MC4 H-level comparison problem and its passage from completed
dg-algebra comparison to completed module-category equivalence; it is
not a second factorization comparison on the evaluation locus.
\end{proposition}

\begin{proof}
The ordered factorization term and the right-hand spectral quantum-group
term in~\eqref{eq:triple-equivalence} are fixed by the assumed DK-3
outer equivalence, so after DK-3 the only missing part of the desired
triple equivalence is the middle equivalence
\[
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\simeq
\operatorname{Rep}^{\mathrm{spec}}\!
 \bigl(\QGspec(R_{\cA})\bigr)^{\mathrm{op}}.
\]
Corollary~\ref{cor:yangian-hlevel-comparison-criterion} shows that, once
$\Ydg_{\cA}$ carries a separated complete RTT-adapted filtration with
the theorematic finite RTT quotients, the underlying completed dg
algebra comparison with the standard RTT completion becomes formal.
Thus the remaining mathematical content is precisely the MC4
construction of that filtered H-level target together with the passage
from the dg comparison to the completed module-category equivalence
displayed above. This is exactly the DK-4/DK-5 remainder.
\end{proof}

\begin{remark}[Application to the full bridge conjecture]
\label{rem:yangian-dk-mc4-reduction-application}
Proposition~\ref{prop:yangian-dk-mc4-reduction} isolates the Yangian
residue inside Conjecture~\ref{conj:full-dk-bridge}: once the outer
factorization equivalence is supplied, what remains is the
RTT-adapted H-level realization and the completed
module-category equivalence.
\end{remark}

%% ================================================================
%% The Bridge Theorem package
%% ================================================================
\begin{remark}[The Bridge Theorem package]
\label{rem:bridge-theorem-programme}
\index{Bridge Theorem!package|textbf}
\index{Drinfeld--Kohno!Bridge Theorem package}
We decompose
Conjecture~\ref{conj:full-dk-bridge} (the \textbf{Bridge
Theorem} target) into four sub-targets and six lemmas.

\smallskip\noindent
The triple equivalence~\eqref{eq:triple-equivalence} asserts that
three deformation-theoretic presentations are matched:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the MC problem for the \emph{factorization convolution algebra}
 $\operatorname{Conv}_{\Eone}(\bar B(\cA), \cA^!)$ on ordered configuration
 spaces, presenting~$\Factord$;
\item the completed MC problem for the \emph{Yangian convolution algebra}
 $\widehat{\operatorname{Conv}}(\bar B(Y), Y^!)$, producing
 the dg-side category
 $\operatorname{Mod}^{\mathrm{comp}}(\Ydg_\cA)$; and
\item the \emph{spectral quantum-group presentation}
 $\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_\cA))$.
\end{enumerate}
Each sub-target B1--B4 below is a specific extension, completion, or
identification problem. The proved core (Lemmas~1--2) establishes
the deformation-theoretic equivalence on the evaluation-generated
locus; the open targets extend it to the full highest-weight
category, complete the pronilpotent tower on the dg side, and
identify the spectral quantum-group presentation.

\medskip\noindent
\textbf{Four sub-targets.}
\begin{enumerate}[label=\textup{B\arabic*.}]
\item \label{item:B1}
 \emph{Full $\mathcal{O}$-Koszul extension.}
 The Yangian is Koszul on the full category~$\mathcal{O}$, not only
 on the evaluation locus. Then the bar spectral sequence collapses,
 minimal resolutions exist for all highest-weight objects, and
 the duality extends from evaluation modules to
 $D^b(\mathcal{O}_{Y_\hbar}) \simeq D^b(\mathcal{O}_{Y_{-\hbar}})$.
 (Extends Remark~\ref{rem:yangian-dk23-inputs}.)

\item \label{item:B2}
 \emph{Yangian tower completion.}
 The four checks of Remark~\ref{rem:yangian-mc4-checklist}:
 (1)~finite RTT truncations in the proved $\Eone$-Koszul regime;
 (2)~compatible descent of finite-stage bar/cobar;
 (3)~Mittag--Leffler on $\{H^m(\bar B(Y_{\le N}))\}_N$;
 (4)~H-level comparison with an RTT-adapted dg model.
 Items~(1)--(3) are theorematic for the standard RTT tower; item~(4)
 is the genuine hard residue that upgrades the standard RTT
 completion to the desired H-level dg model.
 (Proposition~\ref{prop:yangian-tower-mc4-criterion}.)

\item \label{item:B3}
 \emph{Boundary/line realization.}
 There is a sufficiently rich holomorphic boundary condition~$b$
 with boundary chiral algebra~$V_b$, a line-to-boundary comparison
 functor
 $F_b \colon \mathcal{C}_T \to V_b\text{-mod}$,
 and a compatible line-side algebraic/spectral package controlled by
 a dg-shifted Yangian.
 The benchmark families provide only calibration and prototype
 evidence for this package, not a theorematic realization of
 $F_b$ in general.
 (Fresh input: Costello--Dimofte--Gaiotto~\cite{CDG2023},
 Dimofte--Niu--Py~\cite{DNP25}.)

\item \label{item:B4}
 \emph{Spectral quantum-group comparison.}
 The open spectral comparison is to identify the boundary spectral
 $R$-matrix data furnished by such a boundary/line package with
 Latyntsev's factorization quantum-group package
 \cite{Latyntsev23}; on that surface the middle category identifies with
 $\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))$.
\end{enumerate}

\medskip\noindent
\textbf{Six-lemma architecture.}
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{clll}
\textbf{Lemma} & \textbf{Content} & \textbf{Status} & \textbf{Input} \\
\hline
1 & Evaluation-locus factorization bridge
 & \textbf{Proved} & Thm~\ref{thm:factorization-dk-eval} \\
2 & Verdier $= R^{-1}$
 & \textbf{Proved} & Thm~\ref{thm:derived-dk-yangian} \\
3 & Category~$\mathcal{O}$ extension
 & Open & Needs B1 \\
4 & Tower completion
 & Open & Needs B2 \\
5 & Boundary/line equivalence $F_b$
 & Open & Needs B3 \\
6 & Spectral quantum-group identification
 & Open & Needs B4 \\
\end{tabular}
\end{center}
\emph{Lemmas~1--2 are proved. Lemmas~3--6 are the kill targets.}
Once all six close, the full Bridge Theorem
(Conjecture~\ref{conj:full-dk-bridge}) is done.

\medskip\noindent
\textbf{Benchmark ladder} (fixed order, without skipping):
\[
\beta\gamma\text{/Heis}
\;\to\; \hat{\mathfrak{sl}}_2
\;\to\; Y(\mathfrak{sl}_2)
\;\to\; Y(\mathfrak{sl}_3)
\;\to\; Y(\mathfrak{sl}_N)\text{ cat-}\mathcal{O}
\;\to\; \text{shifted Yangian tower.}
\]
Toroidal and elliptic extensions come only after the tower theorem
exists.
\end{remark}

\begin{theorem}[Bridge Criterion Theorem; \ClaimStatusProvedHere]
\label{thm:bridge-criterion}
\index{Bridge Theorem!criterion theorem|textbf}
Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \textup{B1}:
 the full category-$\mathcal{O}$ Koszul extension package on the
 Yangian side: the bar spectral sequence collapses for all
 highest-weight objects, minimal resolutions exist, and the resulting
 bar/cobar comparison extends from evaluation modules to the full
 highest-weight category;
\item \textup{B2}:
 theorematic finite RTT truncations in the proved $\Eone$-Koszul
 regime, compatible descent of finite-stage bar/cobar, Mittag--Leffler
 stabilization on $\{H^m(\bar B(Y_{\le N}))\}_N$, inverse-limit
 identification of the completed RTT tower, and the H-level
 realization/comparison packet identifying that standard completion
 with the dg-shifted Yangian~$\Ydg_{\cA}$; and
\item \textup{B4}:
 the spectral quantum-group comparison identifying the middle
 category with Latyntsev's factorization quantum-group
 category~\cite{Latyntsev23}.
\end{enumerate}
Then there are equivalences of braided monoidal stable
$\infty$-categories
\[
\Factord(X;\cA)
\;\simeq\;
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\;\simeq\;
\operatorname{Rep}^{\mathrm{spec}}\!
 \bigl(\QGspec(R_{\cA})\bigr)^{\mathrm{op}},
\]
compatible with evaluation modules and the KZ monodromy package on the
evaluation locus,
with Verdier duality acting by $R_{\cA} \mapsto R_{\cA}^{-1}$.
\end{theorem}

\begin{proof}
The argument combines the proved evaluation-locus factorization bridge
with the later dg-side completion and spectral-comparison stages.

\emph{Step~1: Evaluation-locus factorization bridge.}
By Theorem~\ref{thm:factorization-dk-eval} (Lemma~1), the
bar-cobar functor induces an equivalence on the evaluation-generated
factorization subcategory:
the twisting morphism
$\tau \in \operatorname{Conv}(\bar B(\cA),\cA^!)$ restricts on evaluation objects
to the Kazhdan twisting morphism, and Verdier duality reverses
collision-cycle orientation, inverting $R_\cA$ (Lemma~2).
This establishes the bridge on the evaluation-generated
parameters.

\emph{Step~2: Extension beyond the evaluation-generated locus.}
Under B1 (the full category-$\mathcal{O}$ Koszul extension package),
the bar spectral sequence collapses for all highest-weight objects,
minimal resolutions exist, and the bar/cobar comparison extends from
the evaluation-generated subcategory to the full highest-weight
category (Lemma~3).

\emph{Step~3: Pronilpotent MC completion.}
Under B2 (tower completion), the pronilpotent MC tower
$\{\operatorname{Conv}(\bar B(Y_{\le N}), Y_{\le N}^!)\}_N$ converges:
the inverse limit of finite RTT stages realizes the standard completed
bar object and the corresponding standard RTT completion
\textup{(}Proposition~\ref{prop:yangian-tower-mc4-criterion},
Corollary~\ref{cor:yangian-standard-mc4-package}\textup{)}. The
H-level realization/comparison packet then identifies that standard
completion with the dg-shifted Yangian~$\Ydg_{\cA}$
\textup{(}Corollary~\ref{cor:yangian-hlevel-comparison-criterion}\textup{)}, so
$\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})$ becomes an actual
completed dg-side category rather than formal target data (Lemma~4).

\emph{Step~4: Spectral comparison.}
Under B4 (the spectral quantum-group comparison), the resulting
completed dg-side category is identified with the spectral
quantum-group side attached to the compared spectral datum in the sense
of Latyntsev~\cite{Latyntsev23}, namely with
$\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}$
(Lemma~6).

The broader boundary/line route surrounding B3 provides an
independent route to B4 by
combining three separate ingredients on the boundary side: the
line-to-boundary comparison $F_b$, the derived-center recovery map
$\beta_{\mathrm{der}}$ back to the bulk algebra, and the additional
spectral $R$-matrix identification on $V_b$-mod.

The separate degree-$2$ shadow assertion
$r(z)=\tau|_{\deg 2}$ is not part of the present criterion theorem;
it remains the additional benchmark package isolated in
Remark~\ref{rem:r-from-tau}.
\end{proof}

\begin{remark}[Criterion form of the bridge conjecture]
\label{rem:bridge-criterion-application}
Theorem~\ref{thm:bridge-criterion} is the formal implication behind
Conjecture~\ref{conj:full-dk-bridge}: once the three named inputs B1,
B2, and B4 are verified, the triple equivalence follows without any
additional Yangian calculation. The separate propagator-shadow
benchmark $r(z)=\tau|_{\deg 2}$ remains the additional comparison
package isolated in Remark~\ref{rem:r-from-tau}.
\end{remark}

\begin{remark}[B1 obstruction: thick generation does not imply
\texorpdfstring{$\mathcal{O}$}{O}-Koszulness]
\label{rem:b1-obstruction-analysis}
\index{Bridge Theorem!B1 obstruction analysis}
\index{Koszulness!category O obstruction}
The homological core of B1
\textup{(}Yangian Koszulness on the full
category~$\mathcal{O}$\textup{)} does \emph{not} follow from thick generation by
evaluation modules (Corollary~\ref{cor:dk2-thick-generation-all-types}) combined
with evaluation-locus Koszulness
(Proposition~\ref{prop:yangian-koszul}), for a precise structural reason.

\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{What MC3 gives.}
 Thick generation (Corollary~\ref{cor:dk2-thick-generation-all-types})
 says every object of
 $D^b(\mathcal{O}^{\mathrm{eval}})$
 is built from evaluation modules by cones and retracts. The DK
 equivalence extends to this thick subcategory (DK-2/3,
 Corollary~\ref{cor:dk23-all-types}) \emph{without} requiring bar
 spectral sequence collapse on non-evaluation objects. The argument
 uses sectorwise convergence and cosheaf descent, bypassing Ext
 concentration entirely.

\item \emph{What B1 asks.}
 Koszulness on the full category~$\mathcal{O}$ means: for every
 pair of highest-weight modules $M$, $N$ in~$\mathcal{O}_{Y_\hbar}$,
 the bar spectral sequence computing $\Ext^*_Y(M, N)$
 collapses at~$E_2$. This is an Ext diagonal concentration
 condition: the Ext algebra
 $\Ext^*_{\mathcal{O}}(S, S)$ (with $S$ the direct sum of simple
 objects) should be generated in degree~$1$.

\item \emph{The gap.}
 Thick-subcategory closure does not preserve Ext concentration.
 If $L$ is built as a cone $L = \operatorname{cone}(f\colon V_1 \to V_2)$
 of evaluation modules, the long exact Ext sequence gives
 $\Ext^i(L, M)$ as a sub-quotient of $\Ext^i(V_j, M)$,
 but the connecting maps may introduce nontrivial higher-Ext
 contributions even when $\Ext^*(V_j, M)$ is concentrated. In
 particular, infinite-dimensional highest-weight modules (Verma
 modules, prefundamental modules~$L^-$) can have Ext groups that
 fail to concentrate, despite lying in the thick closure of
 evaluation modules.

\item \emph{Francis--Gaitsgory completion.}
 The FG pro-nilpotent completion
 (Remark~\ref{rem:francis-gaitsgory-mc3}) extends a
 compact-generator equivalence to the ind-completion. This
 requires the equivalence \emph{on compacts} first, which is
 exactly DK-2/3 on the evaluation-generated core. The extension
 to all highest-weight objects on the module side is a different
 question: it requires B1 (Ext concentration on all of~$\mathcal{O}$).
 The boundary/line path
 (Remark~\ref{rem:boundary-line-bridge-path}) attacks the bridge from
 a different comparison surface rather than proving this
 category-$\mathcal{O}$ extension.
\end{enumerate}

\noindent
\emph{Summary.} The proved DK-2/3 evaluation-generated-core package
closes Lemma~3 of the bridge criterion on that core, which suffices
for the compact-generator version of the bridge. B1 (full
$\mathcal{O}$-Koszulness together with its resulting module-side
extension package) remains the genuinely open input for extending the
equivalence to all highest-weight modules. The
boundary/line path (Remark~\ref{rem:boundary-line-bridge-path})
provides a different route to the spectral comparison side of the
bridge, but on the current theorem surface it complements rather than
replaces B1.
\end{remark}

\begin{remark}[The boundary/line path to the bridge]
\label{rem:boundary-line-bridge-path}
\index{Bridge Theorem!boundary/line path}
\index{line operators!bridge path}
The HT literature offers an independent route to the
bridge. Suppose there is a rich boundary condition~$b$ with
boundary chiral algebra~$V_b$ such that:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $F_b \colon \mathcal{C}_T \to V_b\text{-mod}$ is an equivalence
 (the line-side algebraic model is identified with boundary modules);
\item $\beta_{\mathrm{der}} \colon V \to Z(V_b)_{\mathrm{der}}$
 is an isomorphism (bulk data can be recovered from the derived
 center of the boundary algebra).
\end{enumerate}
Then proving the spectral quantum-group identification on
$V_b$-mod is sufficient for the missing comparison
side of the bridge. If $F_b$ is an equivalence, then the line
side algebraic model is already present on $V_b$-mod.
If $\beta_{\mathrm{der}}$ is an isomorphism, the bulk
algebra is recoverable on the derived-center side. Thus the
boundary-module picture supplies the line-side algebraic data together
with a route back to the bulk algebra, while the separate spectral
identification on $V_b$-mod handles the remaining factorization-side
comparison.

This path avoids a direct attack on the spectral comparison by instead
working through the line-side algebraic model, which may be better
behaved. On the current bridge-criterion surface it complements B1
and B2 rather than replacing the category-$\mathcal{O}$ extension.
See Costello--Dimofte--Gaiotto~\cite{CDG2023} and
Dimofte--Niu--Py~\cite{DNP25} for the foundational
boundary/line structure, and Zeng~\cite{KZ2025} for derived-center
evidence.
\end{remark}

\begin{remark}[The $r(z) = \tau|_{\deg 2}$ identification:
MC projection as candidate gluing law]
\label{rem:r-from-tau}
\index{propagator!$r(z) = \tau|_{\deg 2}$}
\index{Chriss--Ginzburg!gluing law}
A natural candidate gluing law between the two sides of the bridge is
the projection of Maurer--Cartan elements between two convolution
algebras recorded below.

The universal MC element $\Theta_\cA \in
\MC(\mathfrak{g}_\cA^{\mathrm{mod}})$
(Proposition~\ref{prop:chriss-ginzburg-structure}) encodes the full
algebra structure of~$\cA$ as a graph sum over stable graphs with
propagator insertions on internal edges
(Definition~\ref{def:modular-bar-hamiltonian}).
Its genus-$0$, degree-$2$ projection is the bar-complex propagator
$\tau \in \operatorname{Conv}(\bar B(\cA), \cA^!)$ on ordered configuration
spaces, with kernel
$\eta_{ij} = d\log(z_i - z_j)$.

The dg-shifted Yangian~$\Ydg_\cA$
(Definition~\ref{def:dg-shifted-yangian}) is governed by its own
MC element $r(z) \in \cA^! \otimes \cA^!(z^{-1})$.
The identification
\[
r(z) = \tau|_{\deg 2}
\]
is the assertion that \emph{the Yangian MC element is the
degree-$2$ shadow of the universal bar-complex MC element}.
In the language of the shadow obstruction tower
(\S\ref{sec:nms-shadow-calculus}), $r(z)$ is the
same-genus, degree-$2$ slice of~$\Theta_\cA$: the scalar
shadow~$\kappa(\cA)$ is the trace of this slice, and $r(z)$ is
the full tensorial content.

This is the single cleanest CG benchmark for the Bridge Theorem
package: compute $\tau|_{\deg 2}$ explicitly in each benchmark
family and verify it matches the known $r$-matrix.
\end{remark}

\begin{proposition}[DK-4 reduction to the fundamental residue packet in
standard type~A; \ClaimStatusProvedHere]
\label{prop:yangian-dk4-typea-frontier}
Assume the hypotheses of
Proposition~\ref{prop:yangian-dk-mc4-reduction} and work with the
standard type-A RTT tower. Then the remaining DK-4 input is reduced to
the boundary-strip identities
\[
\Delta_{a,0}(N)=0
\qquad (0\le a\le N,\ N\ge 0)
\]
for the defects
\[
\Delta_{a,0}(N)
=\mathsf{K}^{\mathrm{line}}_{a,0}(N)
-\mathsf{K}^{\mathrm{RTT}}_{a,0}(N),
\]
together with the standard twisted-coproduct multiplication law on
fundamental evaluation modules. Equivalently, for the standard type-A
tower it is enough to prove the pairwise auxiliary-kernel identity
\[
L_a(u)=R_{0a}(u-a)
\]
on the fundamental evaluation line.

If in addition the one-factor line operator is functorial for the
diagonal $\mathfrak{sl}_M$-action and normalized by
$L_a(u)\to 1$ as $u\to\infty$, then the same DK-4 input is further
reduced to transport of the standard residue formula
\[
\operatorname*{Res}_{u=a}L_a(u)=-\hbar P.
\]
For $M\ge 2$, this transport statement is further reduced to the
ordered mixed-tensor
identity
\[
\Xi_a(e_1\otimes e_2)=-\hbar(e_2\otimes e_1).
\]

By
Proposition~\ref{prop:dg-shifted-rtt-typea-uniform-single-line},
this single ordered tensor-line computation already determines the full
residue operator $\Xi_a=-\hbar P$ uniformly in the rank.
Proposition~\ref{prop:dg-shifted-rtt-standard-typea-local-packet}
shows that this residue formula already holds on the theorematic
standard RTT tower itself. Thus the genuinely live local input is to
identify the dg-shifted or factorization one-factor kernel with that
standard normalized residue, equivalently with the same mixed-tensor
matrix coefficient on the fundamental line.

Under one-loop exactness,
Proposition~\ref{prop:dg-shifted-rtt-degree2-mixed-tensor-criterion}
reduces this transport problem further to the ordered mixed-tensor
coefficient of the degree-$2$ twisting morphism $r(z)=\tau|_{\deg 2}$.
Corollary~\ref{prop:dg-shifted-rtt-seed-normalized-coefficient}
shows that, in the standard logarithmic normalization, this is
equivalently the ordered mixed-tensor coefficient of the operator
$r_a^{\mathrm{fund}}(z)$ itself.

Proposition~\ref{prop:dg-shifted-rtt-degree2-scalar-normalization}
then removes the remaining one-loop matrix ambiguity: after
degree-$2$ scalar normalization, the only genuinely live datum is the
scalar coefficient of the permutation operator. In particular,
Corollary~\ref{prop:dg-shifted-rtt-degree2-casimir-normalization}
shows that the trace-zero convention
$P-\frac{1}{M}\id$ reduces to the same scalar packet, and
Proposition~\ref{prop:dg-shifted-rtt-degree2-fundamental-casimir}
computes that scalar as $-1$ once the standard fundamental Casimir
insertion is identified.
Corollary~\ref{prop:factorization-fundamental-casimir-identity} proves
that the factorization side already satisfies this identity, and
Proposition~\ref{prop:dg-shifted-factorization-shared-seed} shows that
any dg-shifted realization presented by the same ordered bar seed
inherits the same coefficient. Thus the genuinely live local step is
no longer a new coefficient computation, but the realization of the
dg-shifted target with that shared bar seed.
\end{proposition}

\begin{proof}
By Proposition~\ref{prop:yangian-dk-mc4-reduction}, once DK-3 is fixed
the remaining work is to construct a dg-shifted Yangian with an
RTT-adapted filtration satisfying
Corollary~\ref{cor:yangian-hlevel-comparison-criterion}. The finite
quotient comparison required there is reduced by
Proposition~\ref{prop:dg-shifted-rtt-oneloop-kernel-criterion} to the
coefficient identities
$\mathsf{K}^{\mathrm{line}}_{a,b}(N)
=\mathsf{K}^{\mathrm{RTT}}_{a,b}(N)$,
by Proposition~\ref{prop:dg-shifted-rtt-boundary-seed} to the boundary
strip $\Delta_{a,0}(N)$, and by
Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation} to the
fundamental evaluation family together with the standard
twisted-coproduct multiplication law.

Proposition~\ref{prop:dg-shifted-rtt-auxiliary-kernel-criterion} then
reduces this boundary-strip packet to the pairwise kernel identity
$L_a(u)=R_{0a}(u-a)$ on the fundamental line. Under the symmetry and
normalization hypotheses,
Corollary~\ref{cor:dg-shifted-rtt-typea-residue-reduction} reduces that
identity to the residue formula
$\operatorname*{Res}_{u=a}L_a(u)=-\hbar P$, and
Corollary~\ref{cor:dg-shifted-rtt-typea-single-line} reduces the
transport-normalized residue formula further to the ordered
mixed-tensor check displayed in
the statement, while
Proposition~\ref{prop:dg-shifted-rtt-typea-uniform-single-line}
shows that this one check already determines the whole residue
operator uniformly in~$M$. Proposition~\ref{prop:dg-shifted-rtt-standard-typea-local-packet}
then identifies that residue explicitly on the theorematic standard
RTT side.
\end{proof}

\begin{remark}[Remaining type-$A$ DK frontier]
After DK-3, the live analytic input on the standard type-$A$ tower is
the H-level dg-shifted realization together with the compact-core
DK-5 packet. Proposition~\ref{prop:dg-shifted-rtt-standard-typea-local-packet}
shows that no new residue coefficient remains to be computed inside
the standard RTT tower itself.
\end{remark}

\begin{proposition}[DK-5 reduction to compact-generator comparison;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-compact-generators}
Assume the hypotheses of
Proposition~\ref{prop:yangian-dk4-typea-frontier}. Let
\[
\mathcal{G}^{\mathrm{fund}}_{Y}
\subset \operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA}),
\qquad
\mathcal{G}^{\mathrm{fund}}_{q}
\subset \operatorname{Rep}^{\mathrm{spec}}\!
 \bigl(\QGspec(R_{\cA})\bigr)^{\mathrm{op}}
\]
be the full subcategories generated by the completed images of finite
ordered tensor products of fundamental evaluation modules. Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item both ambient stable categories are compactly generated, and
 their compact objects are the thick idempotent-complete closures of
 $\mathcal{G}^{\mathrm{fund}}_{Y}$ and
 $\mathcal{G}^{\mathrm{fund}}_{q}$, respectively;
\item the DK-4 comparison supplies an exact colimit-preserving functor
 \[
 F_{\mathrm{comp}}\colon
 \operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
 \longrightarrow
 \operatorname{Rep}^{\mathrm{spec}}\!
 \bigl(\QGspec(R_{\cA})\bigr)^{\mathrm{op}}
 \]
 compatible with the dg comparison
 $\Ydg_{\cA}\xrightarrow{\sim}\widehat Y_{\mathrm{RTT}}$ and with the
 DK-3 transport on the evaluation-generated packet; and
\item the restriction of $F_{\mathrm{comp}}$ to
 $\mathcal{G}^{\mathrm{fund}}_{Y}$ is an equivalence onto
 $\mathcal{G}^{\mathrm{fund}}_{q}$.
\end{enumerate}
Then $F_{\mathrm{comp}}$ is an equivalence of stable categories. In
particular, after DK-4 the remaining DK-5 input is the compact-generator
comparison on the completed module categories; the passage from that
packet to the full completed equivalence is formal.
\end{proposition}

\begin{proof}
By assumption~\textup{(iii)}, the functor
$F_{\mathrm{comp}}$ is an equivalence on the chosen generator packet.
Because $F_{\mathrm{comp}}$ is exact, it preserves shifts, cones, and
direct summands, so it is an equivalence on the thick idempotent-complete
closures of that packet. Assumption~\textup{(i)} identifies those
closures with the compact objects in the two ambient categories.

Now both categories are compactly generated, and
$F_{\mathrm{comp}}$ preserves colimits by assumption~\textup{(ii)}.
Hence the same uniqueness-of-extension mechanism used in the proof of
Theorem~\ref{thm:chiral-co-contra-correspondence} applies: an exact
colimit-preserving functor between compactly generated stable
categories is determined by its restriction to compact generators, and
an equivalence on those generators extends to an equivalence on the
whole categories. Therefore $F_{\mathrm{comp}}$ is an equivalence.
\end{proof}

\begin{proposition}[Compact-core comparison reduces to the completed
fundamental packet; \ClaimStatusProvedHere]
\label{prop:yangian-dk5-fundamental-packet}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-compact-generators}. Write
\[
\mathcal{C}_Y^\omega
:=
\operatorname{thick}^{\mathrm{idemp}}
\bigl(\mathcal{G}^{\mathrm{fund}}_{Y}\bigr),
\qquad
\mathcal{C}_q^\omega
:=
\operatorname{thick}^{\mathrm{idemp}}
\bigl(\mathcal{G}^{\mathrm{fund}}_{q}\bigr)
\]
for the compact cores of the two completed categories, and let
\[
\mathcal{P}^{\mathrm{fund}}_{Y}\subset \mathcal{C}_Y^\omega,
\qquad
\mathcal{P}^{\mathrm{fund}}_{q}\subset \mathcal{C}_q^\omega
\]
be the full subcategories spanned by the completed fundamental
evaluation modules themselves. Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item each compact core is the smallest full stable
 idempotent-complete braided monoidal subcategory containing its
 completed fundamental packet;
\item there exist exact braided monoidal functors
 \[
 KZ^\omega_{\mathrm{comp}}\colon
 \mathcal{C}_Y^\omega \to \mathcal{C}_q^\omega,
 \qquad
 LZ^\omega_{\mathrm{comp}}\colon
 \mathcal{C}_q^\omega \to \mathcal{C}_Y^\omega;
 \]
\item the restrictions of these functors to
 $\mathcal{P}^{\mathrm{fund}}_{Y}$ and
 $\mathcal{P}^{\mathrm{fund}}_{q}$ recover the DK-3 transport on the
 completed fundamental evaluation packet; and
\item both composites
 \[
 LZ^\omega_{\mathrm{comp}} \circ KZ^\omega_{\mathrm{comp}},
 \qquad
 KZ^\omega_{\mathrm{comp}} \circ LZ^\omega_{\mathrm{comp}}
 \]
 are naturally isomorphic to the identity on the completed
 fundamental packets.
\end{enumerate}
Then the two functors are quasi-inverse exact braided monoidal
equivalences
\[
KZ^\omega_{\mathrm{comp}}\colon
\mathcal{C}_Y^\omega \xrightarrow{\sim} \mathcal{C}_q^\omega,
\qquad
LZ^\omega_{\mathrm{comp}}\colon
\mathcal{C}_q^\omega \xrightarrow{\sim} \mathcal{C}_Y^\omega.
\]

Equivalently, once the compact cores are generated by completed
fundamental evaluation modules, the compact-core DK-5 packet is forced
by transport on that completed fundamental packet.
\end{proposition}

\begin{proof}
This is the compact-core analogue of
Proposition~\ref{prop:yangian-dk3-generated-core}. By
assumption~\textup{(i)}, each compact core is obtained from its
completed fundamental packet by finite iterates of shifts, cones,
direct summands, and ordered tensor products. Exact braided monoidal
functors preserve each of these operations. Therefore any natural
transformation between exact braided monoidal functors that is an
isomorphism on the completed fundamental packet remains an isomorphism
on the full compact core.

Apply this to the two composites in assumption~\textup{(iv)}. Since
they are naturally isomorphic to the identity on the completed
fundamental packets, they are naturally isomorphic to the identity on
$\mathcal{C}_Y^\omega$ and $\mathcal{C}_q^\omega$. Hence
$KZ^\omega_{\mathrm{comp}}$ and $LZ^\omega_{\mathrm{comp}}$ are
quasi-inverse exact braided monoidal equivalences.
\end{proof}

\begin{proposition}[DK-5 comparison functor is the ind-extension of the
compact core; \ClaimStatusProvedHere]
\label{prop:yangian-dk5-ind-extension}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-compact-generators}. Write
\[
\mathcal{C}_Y^\omega
:=
\operatorname{thick}^{\mathrm{idemp}}
\bigl(\mathcal{G}^{\mathrm{fund}}_{Y}\bigr),
\qquad
\mathcal{C}_q^\omega
:=
\operatorname{thick}^{\mathrm{idemp}}
\bigl(\mathcal{G}^{\mathrm{fund}}_{q}\bigr)
\]
for the compact cores of the two completed categories. Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the ambient categories
 $\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})$ and
 $\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}$
 are presentable, stable, and compactly generated, with compact
 objects exactly $\mathcal{C}_Y^\omega$ and $\mathcal{C}_q^\omega$;
\item there is an exact equivalence
 \[
 F^\omega\colon \mathcal{C}_Y^\omega \xrightarrow{\sim} \mathcal{C}_q^\omega
 \]
 whose restriction to the completed fundamental evaluation packet
 agrees with the DK-3 transport on the evaluation-generated core.
\end{enumerate}
Then there exists a unique exact colimit-preserving equivalence
\[
\operatorname{Ind}(F^\omega)\colon
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\xrightarrow{\sim}
\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}
\]
extending $F^\omega$.

In particular, once the compact-core equivalence is constructed, the
comparison functor appearing in
Proposition~\ref{prop:yangian-dk5-compact-generators} and its
compatibility with DK-3 on the compact generator packet are formal.
\end{proposition}

\begin{proof}
By assumption~\textup{(i)}, each ambient category is the
ind-completion of its compact objects:
\[
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\simeq
\operatorname{Ind}(\mathcal{C}_Y^\omega),
\qquad
\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}
\simeq
\operatorname{Ind}(\mathcal{C}_q^\omega).
\]
This is the same compact-generation mechanism used in
Theorem~\ref{thm:ind-completed-extension}: a presentable stable
compactly generated category is recovered from its compact part by
ind-completion.

Now apply the universal property of ind-completion to the exact
equivalence $F^\omega$. It extends uniquely to an exact
colimit-preserving functor
\[
\operatorname{Ind}(F^\omega)\colon
\operatorname{Ind}(\mathcal{C}_Y^\omega)
\longrightarrow
\operatorname{Ind}(\mathcal{C}_q^\omega),
\]
and because $F^\omega$ is already an equivalence, its ind-extension is
an equivalence as well. Transporting along the displayed
identifications of the ambient categories yields the claimed functor.

The final sentence is immediate: once the compact-core equivalence is
fixed, the completed comparison functor is forced to be this unique
ind-extension, so no separate completed-level functor construction
remains.
\end{proof}

\begin{corollary}[DK-5 reduces to the compact-core equivalence;
\ClaimStatusProvedHere]
\label{cor:yangian-dk5-compact-core}
Assume the hypotheses of
Corollary~\ref{prop:yangian-typea-dg-local-closure}. Assume further
that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the completed dg-shifted and spectral categories are presentable,
 stable, and compactly generated;
\item their compact objects are the thick idempotent-complete closures
 of the completed fundamental evaluation packets; and
\item those compact cores are exactly equivalent in a way compatible
 with DK-3 on the completed fundamental packet.
\end{enumerate}
Then the standard type-$A$ Yangian DK-5 packet closes.

Equivalently, after the local dg-shifted packet is closed, the
remaining DK-5 input is exactly the compact-core equivalence; the
completed comparison functor itself is formal.
\end{corollary}

\begin{proof}
Under
Corollary~\ref{prop:yangian-typea-dg-local-closure}, the local DK-4
packet is already closed, so only DK-5 remains. Assumptions
\textup{(i)}--\textup{(iii)} are precisely the hypotheses of
Proposition~\ref{prop:yangian-dk5-ind-extension}, which produces the
unique exact colimit-preserving equivalence between the completed
categories. This is exactly the DK-5 conclusion.
\end{proof}

\begin{corollary}[DK-5 reduces to compact generation plus completed
fundamental-packet transport; \ClaimStatusProvedHere]
\label{cor:yangian-dk5-fundamental-packet}
Assume the hypotheses of
Corollary~\ref{prop:yangian-typea-dg-local-closure}. Assume further
that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the completed dg-shifted and spectral categories are presentable,
 stable, and compactly generated;
\item their compact objects are the smallest full stable
 idempotent-complete braided monoidal subcategories containing the
 completed fundamental evaluation packets; and
\item there exist exact braided monoidal functors between those compact
 cores whose restrictions to the completed fundamental evaluation
 packets recover the DK-3 transport and whose composites are the
 identity on that packet.
\end{enumerate}
Then the standard type-$A$ Yangian DK-5 packet closes.

Equivalently, once the local dg-shifted packet is closed, the remaining
categorical input is compact generation together with transport on the
completed fundamental evaluation packet; the compact-core equivalence
and the ambient completed comparison functor are then formal.
\end{corollary}

\begin{proof}
Assumption~\textup{(ii)} identifies the compact objects with the
compact cores appearing in
Proposition~\ref{prop:yangian-dk5-fundamental-packet}. By
assumption~\textup{(iii)}, that proposition yields an exact
equivalence between the compact cores. Now apply
Proposition~\ref{prop:yangian-dk5-ind-extension} to extend that
compact-core equivalence uniquely to an exact colimit-preserving
equivalence of the ambient completed categories. This is exactly the
DK-5 conclusion.
\end{proof}

\begin{proposition}[Compact-core DK-5 functors from realization of a
finite-dimensional factorization DK pair; \ClaimStatusProvedHere]
\label{prop:yangian-dk5-core-realization}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-fundamental-packet}. Let
\[
KZ_{\mathrm{fd}}\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\xrightarrow{\sim}
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
\[
LZ_{\mathrm{fd}}\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\xrightarrow{\sim}
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\]
be quasi-inverse exact braided monoidal equivalences whose restrictions
to the finite-dimensional fundamental evaluation packet recover the
standard type-$A$ DK transport on that packet. Assume there exist exact braided
monoidal equivalences
\[
\quad
J_Y^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\xrightarrow{\sim}
\mathcal{C}_Y^\omega,
\qquad
J_q^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\xrightarrow{\sim}
\mathcal{C}_q^\omega
\]
whose restrictions to the evaluation generators identify them with the
completed fundamental evaluation packets
$\mathcal{P}^{\mathrm{fund}}_{Y}$ and
$\mathcal{P}^{\mathrm{fund}}_{q}$.
Then
\[
KZ^\omega_{\mathrm{comp}}
:=
J_q^\omega \circ KZ_{\mathrm{fd}} \circ (J_Y^\omega)^{-1},
\qquad
LZ^\omega_{\mathrm{comp}}
:=
J_Y^\omega \circ LZ_{\mathrm{fd}} \circ (J_q^\omega)^{-1}
\]
are quasi-inverse exact braided monoidal equivalences
\[
\mathcal{C}_Y^\omega \xrightarrow{\sim} \mathcal{C}_q^\omega
\]
whose restrictions to the completed fundamental evaluation packets
recover the DK-3 transport. In particular, the packet hypotheses of
Proposition~\ref{prop:yangian-dk5-fundamental-packet} are automatic.
\end{proposition}

\begin{proof}
The displayed functors are composites of exact braided monoidal
equivalences, hence are themselves exact braided monoidal
equivalences. Because the completion equivalences
$J_Y^\omega$ and $J_q^\omega$ identify the evaluation generators with
the completed fundamental evaluation packets, the restrictions of
$KZ^\omega_{\mathrm{comp}}$ and $LZ^\omega_{\mathrm{comp}}$ to those
packets are exactly the transported DK-3 packet and its inverse. Therefore the
composites are the identity on the completed fundamental packets, and
the final sentence follows immediately.
\end{proof}

\begin{lemma}[Finite-dimensional Yangian factorization core is
generated by fundamental evaluation objects; \ClaimStatusProvedHere]
\label{lem:yangian-fd-fundamental-generation}
For $\mathfrak{sl}_M$, the braided monoidal stable category
\[
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\]
is the smallest full stable idempotent-complete braided monoidal
subcategory containing the fundamental evaluation objects.
\end{lemma}

\begin{proof}
By Proposition~\ref{prop:dk2-thick-generation-typeA}, every
finite-dimensional irreducible Yangian module is a subquotient of a
tensor product of fundamental evaluation modules. Applying
Lemma~\ref{lem:composition-thick-generation} to the abelian category of
finite-dimensional Yangian modules shows that the bounded derived
category is the thick triangulated closure of those fundamental
evaluation modules. The factorization category
\[
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\]
is this same finite-dimensional stable category equipped with the
ordered factorization tensor product, and ordered tensor products of
fundamental evaluation objects remain inside the same closure.
Therefore the smallest full stable idempotent-complete braided
monoidal subcategory containing the fundamental evaluation objects is
the whole finite-dimensional Yangian factorization category.
\end{proof}

\begin{lemma}[Finite-dimensional quantum-group factorization core is
generated by fundamental evaluation objects; \ClaimStatusProvedHere]
\label{lem:quantum-fd-fundamental-generation}
For $\mathfrak{sl}_M$, the braided monoidal stable category
\[
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
is the smallest full stable idempotent-complete braided monoidal
subcategory containing the fundamental evaluation objects.
\end{lemma}

\begin{proof}
Finite-dimensional irreducible type-$A$ quantum-loop modules are
classified by their Drinfeld polynomials / highest $\ell$-weights, and
factoring those polynomials into linear terms expresses every simple as
a subquotient of an ordered tensor product of fundamental evaluation
modules (\cite[Ch.~12]{ChariPressley94}, \cite[\S2]{Hernandez05}).
Applying Lemma~\ref{lem:composition-thick-generation} to the abelian
category of finite-dimensional quantum-loop modules shows that the
bounded derived category is the thick triangulated closure of the
fundamental evaluation modules. The factorization category
\[
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
is this same finite-dimensional stable category equipped with the
ordered factorization tensor product, and ordered tensor products of
fundamental evaluation objects remain inside the same closure.
Therefore the smallest full stable idempotent-complete braided
monoidal subcategory containing the fundamental evaluation objects is
the whole finite-dimensional quantum-group factorization category.
\end{proof}

\begin{proposition}[Spectral compact-core realization is formal from
generator transport; \ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-realization-formal}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-fundamental-packet}. Assume
\[
\mathcal{C}_q^\omega
=
\operatorname{thick}^{\mathrm{idemp}}(\mathcal{G}^{\mathrm{fund}}_{q})
\]
is the smallest full stable idempotent-complete braided monoidal
subcategory containing the completed fundamental evaluation packet.
Let
\[
\mathcal{G}^{\mathrm{fund,fd}}_{q}
\subset
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
be the full subcategory generated by finite ordered tensor products of
fundamental evaluation objects, and let
\[
J_q^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\longrightarrow
\mathcal{C}_q^\omega
\]
be an exact braided monoidal functor whose restriction
\[
\mathcal{G}^{\mathrm{fund,fd}}_{q}
\longrightarrow
\mathcal{G}^{\mathrm{fund}}_{q}
\]
is an equivalence onto the completed generator packet. Then
\(J_q^\omega\) is an exact braided monoidal equivalence.

Equivalently, on the spectral side no additional comparison on the full
compact core remains once the generator-level completion transport is
constructed.
\end{proposition}

\begin{proof}
By Lemma~\ref{lem:quantum-fd-fundamental-generation}, the source is the
smallest full stable idempotent-complete braided monoidal subcategory
containing the fundamental evaluation objects. By hypothesis, the
target enjoys the same generation property for the completed
fundamental packet. Because \(J_q^\omega\) is exact and braided
monoidal, it preserves shifts, cones, direct summands, and ordered
tensor products. Since its restriction to
\(\mathcal{G}^{\mathrm{fund,fd}}_{q}\) is already an equivalence onto
\(\mathcal{G}^{\mathrm{fund}}_{q}\), the same thick-closure argument as
in Proposition~\ref{prop:yangian-dk5-compact-generators} upgrades that
equivalence on the generator packet to an equivalence on the thick
idempotent-complete closures. Those closures are exactly the source
and target by Lemma~\ref{lem:quantum-fd-fundamental-generation} and the
displayed hypothesis on \(\mathcal{C}_q^\omega\). Thus \(J_q^\omega\)
is an exact braided monoidal equivalence.
\end{proof}

\begin{proposition}[On the spectral side, ordered tensor-generator
transport is forced by the completed fundamental packet;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-fundamental-packet}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-spectral-realization-formal}. Let
\[
\mathcal{P}^{\mathrm{fund,fd}}_{q}
\subset
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
be the full subcategory spanned by the fundamental evaluation objects
themselves, and let
\[
\mathcal{P}^{\mathrm{fund}}_{q}
\subset
\mathcal{C}_q^\omega
\]
be the full subcategory spanned by their completed spectral images.
Assume that the exact braided monoidal functor
\[
J_q^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\longrightarrow
\mathcal{C}_q^\omega
\]
restricts to an equivalence
\[
\mathcal{P}^{\mathrm{fund,fd}}_{q}
\xrightarrow{\sim}
\mathcal{P}^{\mathrm{fund}}_{q}.
\]
Then its restriction
\[
\mathcal{G}^{\mathrm{fund,fd}}_{q}
\longrightarrow
\mathcal{G}^{\mathrm{fund}}_{q}
\]
is automatically an equivalence onto the completed spectral
generator packet. Consequently, the hypotheses of
Proposition~\ref{prop:yangian-dk5-spectral-realization-formal} are
already satisfied, so \(J_q^\omega\) is an exact braided monoidal
equivalence.

Equivalently, on the spectral side the genuinely non-formal packet is
not the whole ordered tensor-generator family: it is enough to place
the individual fundamental evaluation objects inside the completed
spectral category in an exact braided-monoidal way.
\end{proposition}

\begin{proof}
By Lemma~\ref{lem:quantum-fd-fundamental-generation}, the source
\[
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
is the smallest full stable idempotent-complete braided monoidal
subcategory containing \(\mathcal{P}^{\mathrm{fund,fd}}_{q}\). By the
standing hypothesis of
Proposition~\ref{prop:yangian-dk5-spectral-realization-formal}, the
target \(\mathcal{C}_q^\omega\) enjoys the same generation property for
\(\mathcal{P}^{\mathrm{fund}}_{q}\). Because \(J_q^\omega\) is exact
and braided monoidal, it preserves shifts, cones, direct summands, and
ordered tensor products. Since its restriction to
\(\mathcal{P}^{\mathrm{fund,fd}}_{q}\) is already an equivalence onto
\(\mathcal{P}^{\mathrm{fund}}_{q}\), the same thick-closure argument as
in Proposition~\ref{prop:yangian-dk5-dg-realization-formal} upgrades
that equivalence on the completed fundamental packet to an exact
braided monoidal equivalence on the full finite-dimensional spectral
core.

In particular, the restriction of \(J_q^\omega\) to
\(\mathcal{G}^{\mathrm{fund,fd}}_{q}\) is an equivalence onto
\(\mathcal{G}^{\mathrm{fund}}_{q}\), since those packets are the full
subcategories generated by finite ordered tensor products of the same
fundamental objects on the source and target sides. Therefore the
generator-packet hypothesis of
Proposition~\ref{prop:yangian-dk5-spectral-realization-formal} is
automatic. The final sentence follows.
\end{proof}

\begin{lemma}[Type-\texorpdfstring{$A$}{A} quantum-group fundamental packet is generated
by the vector evaluation line; \ClaimStatusProvedHere]
\label{lem:quantum-fd-vector-fundamental-generation}
Let
\[
\mathcal{P}^{\mathrm{vec,fd}}_{q}
\subset
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
be the full subcategory spanned by the vector evaluation objects.
Then every fundamental evaluation object of
\(\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}\)
belongs to the smallest full stable idempotent-complete braided
monoidal subcategory containing
\(\mathcal{P}^{\mathrm{vec,fd}}_{q}\).

Equivalently, on the finite-dimensional spectral side the full
fundamental packet is generated by the vector evaluation line.
\end{lemma}

\begin{proof}
Each type-$A$ fundamental Kirillov--Reshetikhin module is the image of
the $q$-antisymmetrizer on an ordered tensor power of vector
evaluation modules (\cite[Ch.~12]{ChariPressley94},
\cite[\S2]{Hernandez05}), hence a direct summand. The closure
property follows.
\end{proof}

\begin{proposition}[On the spectral side, the completed fundamental
packet is forced by the completed vector packet;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-vector-packet}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-spectral-fundamental-packet}. Let
\[
\mathcal{P}^{\mathrm{vec,fd}}_{q}
\subset
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
be the full subcategory generated by finite ordered tensor products of
the vector evaluation objects, and
let
\[
\mathcal{P}^{\mathrm{vec}}_{q}
\subset
\mathcal{C}_q^\omega
\]
be the full subcategory generated by the corresponding completed
spectral tensor packet.
Assume that the exact braided monoidal functor
\[
J_q^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\longrightarrow
\mathcal{C}_q^\omega
\]
restricts to an equivalence
\[
\mathcal{P}^{\mathrm{vec,fd}}_{q}
\xrightarrow{\sim}
\mathcal{P}^{\mathrm{vec}}_{q}.
\]
Let
\[
\mathcal{P}^{\mathrm{fund}}_{q}
\subset
\mathcal{C}_q^\omega
\]
be the full subcategory spanned by the standard type-$A$
$q$-antisymmetric direct summands inside finite ordered tensor powers
of \(\mathcal{P}^{\mathrm{vec}}_{q}\), equivalently by the completed
spectral images of the source fundamental evaluation objects. Then
\(J_q^\omega\) restricts to an equivalence
\[
\mathcal{P}^{\mathrm{fund,fd}}_{q}
\xrightarrow{\sim}
\mathcal{P}^{\mathrm{fund}}_{q}.
\]
Consequently the hypotheses of
Proposition~\ref{prop:yangian-dk5-spectral-fundamental-packet} are
already satisfied, so \(J_q^\omega\) is an exact braided monoidal
equivalence.

\end{proposition}

\begin{proof}
By Lemma~\ref{lem:quantum-fd-vector-fundamental-generation}, every
source fundamental evaluation object is a $q$-antisymmetrizer summand
of an ordered tensor power of vector evaluation objects. Since
\(J_q^\omega\) is exact and braided monoidal, it preserves these
summands, giving the equivalence on
\(\mathcal{P}^{\mathrm{fund,fd}}_{q}\). Now apply
Proposition~\ref{prop:yangian-dk5-spectral-fundamental-packet}.
\end{proof}

\begin{proposition}[On the spectral side, ordered vector-packet
transport is forced by the completed vector line;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-vector-line}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-spectral-vector-packet}. Let
\(\mathcal{L}^{\mathrm{vec,fd}}_{q}\) and
\(\mathcal{L}^{\mathrm{vec}}_{q}\) be the full subcategories
spanned by the vector evaluation objects and their completed spectral
images, respectively.
Assume that \(J_q^\omega\)
restricts to an equivalence
\[
\mathcal{L}^{\mathrm{vec,fd}}_{q}
\xrightarrow{\sim}
\mathcal{L}^{\mathrm{vec}}_{q}.
\]
Then on every object of \(\mathcal{P}^{\mathrm{vec,fd}}_{q}\) the
restriction of \(J_q^\omega\) is forced to be the ordered tensor
product of the corresponding completed vector objects, and on the
braid-group operators of the ordered vector packet it is forced to be
the trigonometric braiding of \(\mathcal{C}_q^\omega\)
(once the completed spectral vector line is fixed,
the transport on the whole ordered vector packet carries no additional freedom).
\end{proposition}

\begin{proof}
Since \(\mathcal{P}^{\mathrm{vec,fd}}_{q}\) consists of finite ordered
tensor products of objects of \(\mathcal{L}^{\mathrm{vec,fd}}_{q}\),
braided monoidality of \(J_q^\omega\) forces both the object-level and
braiding-level transport.
\end{proof}

\begin{proposition}[Standard quantum-loop vector seed and additive
log-spectral shifts; \ClaimStatusProvedHere]
\label{prop:quantum-fd-vector-seed-shifts}
Let
\[
V(0)\in \mathcal{L}^{\mathrm{vec,fd}}_{q}
\]
be the vector evaluation object of the quantum loop algebra at
multiplicative spectral parameter \(1\), viewed on the additive
log-spectral line via the exponential coordinate \(z=e^u\). For every
\(a\in \mathbb{C}\), let
\[
\mathsf{T}^{\mathrm{fd}}_a\colon
\mathcal{L}^{\mathrm{vec,fd}}_{q}\xrightarrow{\sim}
\mathcal{L}^{\mathrm{vec,fd}}_{q}
\]
be the pullback along the loop-rotation automorphism \(z\mapsto e^a z\)
of the quantum loop algebra. Then each
\(\mathsf{T}^{\mathrm{fd}}_a\) is an exact braided-monoidal
autoequivalence, and
\[
\mathsf{T}^{\mathrm{fd}}_a(V(0))\cong V(a),
\qquad
\mathsf{T}^{\mathrm{fd}}_{a+b}\cong
\mathsf{T}^{\mathrm{fd}}_a\circ \mathsf{T}^{\mathrm{fd}}_b,
\qquad
\mathsf{T}^{\mathrm{fd}}_0\cong \id .
\]

\end{proposition}

\begin{proof}
Loop rotation \(z\mapsto e^a z\) is a Hopf algebra automorphism of the
quantum loop algebra (\cite[Ch.~12]{ChariPressley94},
\cite[\S2]{Hernandez05}), so pullback defines exact braided-monoidal
autoequivalences. The group law and unit follow from composition.
\end{proof}

\begin{lemma}[Quantum-loop vector seed is Schur-simple;
\ClaimStatusProvedHere]
\label{lem:quantum-fd-vector-seed-schur}
For every \(a\in\mathbb C\), the type-$A$ vector evaluation object
\(V(a)\in \operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}\)
is simple, so \(\End(V(a))\cong \mathbb C\).
\end{lemma}

\begin{proof}
The vector evaluation object is the first fundamental
Kirillov--Reshetikhin module, hence simple (\cite[Ch.~12]{ChariPressley94}).
Schur's lemma gives \(\End(V(a))\cong\mathbb C\).
\end{proof}

\begin{proposition}[On the spectral side, the completed vector line is
forced by one completed vector seed together with spectral shifts;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-vector-seed}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-spectral-vector-line}. Fix one
source vector evaluation object \(V(0)\in
\mathcal{L}^{\mathrm{vec,fd}}_{q}\) and one completed spectral vector
object \(V^\omega(0)\in \mathcal{L}^{\mathrm{vec}}_{q}\). Assume
further that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item for every \(a\in \mathbb{C}\), the source vector evaluation line
 carries an exact braided-monoidal spectral-shift autoequivalence
 \[
 \mathsf{T}^{\mathrm{fd}}_a\colon
 \mathcal{L}^{\mathrm{vec,fd}}_{q}\xrightarrow{\sim}
 \mathcal{L}^{\mathrm{vec,fd}}_{q}
 \]
 with \(\mathsf{T}^{\mathrm{fd}}_a(V(0))\cong V(a)\);
\item for every \(a\in \mathbb{C}\), the completed spectral vector line
 carries an exact braided-monoidal spectral-shift autoequivalence
 \[
 \mathsf{T}^{\omega}_a\colon
 \mathcal{L}^{\mathrm{vec}}_{q}\xrightarrow{\sim}
 \mathcal{L}^{\mathrm{vec}}_{q}
 \]
 with \(\mathsf{T}^{\omega}_a(V^\omega(0))\cong V^\omega(a)\); and
\item the exact braided monoidal functor \(J_q^\omega\) intertwines
 these shift autoequivalences on the vector line:
 \[
 J_q^\omega\circ \mathsf{T}^{\mathrm{fd}}_a
 \cong
 \mathsf{T}^{\omega}_a\circ J_q^\omega
 \qquad (a\in \mathbb{C}),
 \]
 and identifies \(V(0)\) with \(V^\omega(0)\).
\end{enumerate}
Then the restriction of \(J_q^\omega\) to
\(\mathcal{L}^{\mathrm{vec,fd}}_{q}\) is uniquely determined up to
unique natural isomorphism by the image of the single seed object
\(V(0)\) together with the compatible spectral-shift structure.
\end{proposition}

\begin{proof}
The intertwining relation~\textup{(iii)} forces \(J_q^\omega(V(a))
\cong V^\omega(a)\) for every \(a\), since every object of
\(\mathcal{L}^{\mathrm{vec,fd}}_{q}\) is obtained from the seed by
the shift autoequivalences~\textup{(i)}--\textup{(ii)}.
\end{proof}

\begin{proposition}[On the realized spectral vector-line locus, the
completed vector seed and spectral shifts are canonical;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-seed-shift-construction}
Work in the setting of
Propositions~\ref{prop:quantum-fd-vector-seed-shifts}
and~\ref{prop:yangian-dk5-spectral-vector-line}. Assume that the exact
braided monoidal functor
\[
J_q^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\longrightarrow
\mathcal{C}_q^\omega
\]
restricts to an equivalence
\[
\mathcal{L}^{\mathrm{vec,fd}}_{q}\xrightarrow{\sim}
\mathcal{L}^{\mathrm{vec}}_{q}.
\]
Define
\[
V^\omega(0):=J_q^\omega(V(0))
\]
and for each \(a\in\mathbb{C}\) define
\[
\mathsf{T}^{\omega}_a
:=
\left.J_q^\omega\right|_{\mathcal{L}^{\mathrm{vec,fd}}_{q}}
\circ
\mathsf{T}^{\mathrm{fd}}_a
\circ
\left(\left.J_q^\omega\right|_{\mathcal{L}^{\mathrm{vec,fd}}_{q}}\right)^{-1}.
\]
Then each \(\mathsf{T}^{\omega}_a\) is an exact braided-monoidal
autoequivalence of \(\mathcal{L}^{\mathrm{vec}}_{q}\), and
\[
\mathsf{T}^{\omega}_a(V^\omega(0))\cong V^\omega(a),
\qquad
\mathsf{T}^{\omega}_{a+b}\cong
\mathsf{T}^{\omega}_a\circ \mathsf{T}^{\omega}_b,
\qquad
\mathsf{T}^{\omega}_0\cong \id .
\]
In particular, the hypotheses of
Proposition~\ref{prop:yangian-dk5-spectral-vector-seed} are automatic
on any realized spectral vector-line locus (the completed vector seed
and its spectral-shift action are canonically transported from the
standard quantum-loop evaluation line).
\end{proposition}

\begin{proof}
Conjugation by the vector-line equivalence defines
\(\mathsf{T}^{\omega}_a\) on \(\mathcal{L}^{\mathrm{vec}}_{q}\),
and the group law and unit transport from
Proposition~\ref{prop:quantum-fd-vector-seed-shifts} by conjugation.
\end{proof}

\begin{proposition}[On the realized spectral vector-line locus, loop
rotation descends to the full spectral compact core;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-core-shifts}
Work in the setting of
Propositions~\ref{prop:yangian-dk5-spectral-seed-shift-construction}
and~\ref{prop:yangian-dk5-spectral-realization-formal}. Assume that
the exact braided monoidal functor \(J_q^\omega\) restricts to an
equivalence
\[
\mathcal{L}^{\mathrm{vec,fd}}_{q}\xrightarrow{\sim}
\mathcal{L}^{\mathrm{vec}}_{q}.
\]
Let \(\mathsf{T}^{\omega}_a\) be the induced exact braided-monoidal
autoequivalences of the completed vector line from
Proposition~\ref{prop:yangian-dk5-spectral-seed-shift-construction}.
Then each \(\mathsf{T}^{\omega}_a\) extends uniquely to an exact
braided-monoidal autoequivalence, still denoted
\[
\mathsf{T}^{\omega}_a\colon
\mathcal{C}_q^\omega\xrightarrow{\sim}\mathcal{C}_q^\omega,
\]
and these extensions preserve the completed vector packet, completed
fundamental packet, and completed tensor-generator packet. In addition,
\[
\mathsf{T}^{\omega}_{a+b}\cong
\mathsf{T}^{\omega}_a\circ \mathsf{T}^{\omega}_b,
\qquad
\mathsf{T}^{\omega}_0\cong \id
\]
on the full spectral compact core.
\end{proposition}

\begin{proof}
Each \(\mathsf{T}^{\omega}_a\) is exact and braided monoidal on the
completed vector line
(Proposition~\ref{prop:yangian-dk5-spectral-seed-shift-construction}),
hence preserves the ordered vector packet, the completed fundamental
packet (by
Proposition~\ref{prop:yangian-dk5-spectral-vector-packet}), and the
tensor-generator packet. Since
\(\mathcal{C}_q^\omega=
\operatorname{thick}^{\mathrm{idemp}}(\mathcal{G}^{\mathrm{fund}}_{q})\),
uniqueness of thick-closure extension gives the autoequivalence of
\(\mathcal{C}_q^\omega\) and transports the group law.
\end{proof}

\begin{proposition}[Factorization-locus specializations:
\texorpdfstring{$\rho_a$}{rho\_a} pullback, core from vector line,
seed-line forcing; \ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-factorization-shifts}%
\label{prop:yangian-dk5-spectral-factorization-core-from-vector-line}%
\label{prop:yangian-dk5-spectral-factorization-seed-line}%
Work in the setting of
Definitions~\ref{def:ordered-e1-factorization}
and~\ref{def:spectral-quantum-group}. Let
\(J_q^{\mathrm{mult}}\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\longrightarrow
\Factord(\bC^\times;\QGspec(R_{\cA}))\)
be an exact braided-monoidal functor, and write
\(\rho_a\colon \bC^\times\xrightarrow{\sim}\bC^\times\),
\(z\mapsto e^a z\), for the multiplicative dilations.
\begin{enumerate}[label=\textup{(\alph*)}]
\item\emph{Intrinsic loop rotation.}
 Assume the spectral compact core \(\mathcal{C}_q^\omega\) is
 realized as a full stable idempotent-complete braided-monoidal
 subcategory of
 \(\Factord(\bC^\times;\QGspec(R_{\cA}))\) closed under
 \(\rho_a^*\). Then
 \(\mathsf T_a^\omega:=\rho_a^*\colon
 \mathcal C_q^\omega\xrightarrow{\sim}\mathcal C_q^\omega\)
 is an exact braided-monoidal autoequivalence for every
 \(a\in\mathbb C\), with
 \(\mathsf T_{a+b}^\omega\cong
 \mathsf T_a^\omega\circ \mathsf T_b^\omega\) and
 \(\mathsf T_0^\omega\cong \id\).

\item\emph{Core from vector line.}
 Assume \(J_q^{\mathrm{mult}}\) restricts to an equivalence
 \(\mathcal L_q^{\mathrm{vec,fd}}
 \xrightarrow{\sim}
 \mathcal L_q^{\mathrm{vec,mult}}\)
 and each \(\rho_a^*\) preserves
 \(\mathcal L_q^{\mathrm{vec,mult}}\). Let
 \(\mathcal C_{q,\mathrm{mult}}^\omega\) be the smallest full stable
 idempotent-complete braided-monoidal subcategory containing
 \(\mathcal L_q^{\mathrm{vec,mult}}\). Then every \(\rho_a^*\)
 restricts to
 \(\mathcal C_{q,\mathrm{mult}}^\omega\xrightarrow{\sim}
 \mathcal C_{q,\mathrm{mult}}^\omega\),
 \(J_q^{\mathrm{mult}}\) is an exact braided-monoidal equivalence
 \(\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
 \xrightarrow{\sim}
 \mathcal C_{q,\mathrm{mult}}^\omega\),
 and \(\mathcal C_{q,\mathrm{mult}}^\omega\) is a multiplicative
 spectral realization of the spectral compact core.

\item\emph{Seed-line forcing.}
 Fix $V(0)\in \mathcal L_q^{\mathrm{vec,fd}}$ and one ambient
 object
 $V^{\mathrm{mult}}(0)\in
 \Factord(\bC^\times;\allowbreak\QGspec(R_{\cA}))$;
 set
 $V^{\mathrm{mult}}(a):=\rho_a^*V^{\mathrm{mult}}(0)$.
 If $J_q^{\mathrm{mult}}$ restricts to an equivalence on the
 one-object subcategory generated by~$V(0)$ and intertwines
 $\mathsf T_a^{\mathrm{fd}}$ with~$\rho_a^*$ on the source
 vector line, then
 $\mathcal L_q^{\mathrm{vec,fd}}
 \xrightarrow{\sim}
 \mathcal L_q^{\mathrm{vec,mult}}$.
\end{enumerate}
\end{proposition}

\begin{proof}
\textup{(a)}
Each \(\rho_a\) is an automorphism of \(\bC^\times\), so \(\rho_a^*\)
is an exact braided-monoidal autoequivalence of the ambient category.
The closure hypothesis restricts it to \(\mathcal C_q^\omega\), and
\(\rho_{a+b}=\rho_a\circ\rho_b\) gives the group law.

\textup{(b)}
\(\rho_a^*\) preserves the generating line by hypothesis, hence the
thick closure. The source is the thick closure of its vector line
(Lemmas~\ref{lem:quantum-fd-vector-fundamental-generation}
and~\ref{lem:quantum-fd-fundamental-generation}); since
\(J_q^{\mathrm{mult}}\) is exact braided monoidal and an equivalence
on that line, the thick-closure argument of
Proposition~\ref{prop:yangian-dk5-spectral-realization-formal}
upgrades it.

\textup{(c)}
The intertwining forces
\(J_q^{\mathrm{mult}}(V(a))\cong V^{\mathrm{mult}}(a)\), giving
essential surjectivity. Shifts reduce every Hom pair to
\((V(0),V(b-a))\), and the seed equivalence gives full faithfulness.
\end{proof}

\begin{corollary}[One-seed closure: four variants;
\ClaimStatusProvedHere]
\label{cor:yangian-dk5-spectral-seed-realization}%
\label{cor:yangian-dk5-spectral-one-seed}%
\label{cor:yangian-dk5-spectral-factorization-vector-line}%
\label{cor:yangian-dk5-spectral-factorization-ambient-vector-line}%
Each of the following hypotheses forces the full spectral DK-5 packet:
completed vector line, ordered vector packet, completed fundamental
packet, ordered tensor-generator packet, spectral compact core, and
ambient spectral category are all formal.
\begin{enumerate}[label=\textup{(\alph*)}]
\item\emph{Seed-and-shift datum.}
 Work in the setting of
 Propositions~\ref{prop:quantum-fd-vector-seed-shifts}
 and~\ref{prop:yangian-dk5-spectral-realization-formal}. Let
 \(J_q^\omega\) be an exact braided monoidal functor to
 \(\mathcal{C}_q^\omega\). Assume there is a completed vector seed
 \(V^\omega(0)\in \mathcal{C}_q^\omega\), an exact braided-monoidal
 shift family \(\mathsf{T}_a^\omega\) with
 \(\mathsf{T}_{a+b}^\omega\cong
 \mathsf{T}_a^\omega\circ \mathsf{T}_b^\omega\) and
 \(\mathsf{T}_0^\omega\cong \id\), and that setting
 \(V^\omega(a):=\mathsf{T}_a^\omega(V^\omega(0))\), the functor
 \(J_q^\omega\) identifies \(V(0)\) with \(V^\omega(0)\) and
 intertwines source and target shifts. Then \(J_q^\omega\) restricts
 to an equivalence on the vector line and extends to the full compact
 core and its ind-completion.

\item\emph{One multiplicative seed.}
 Work in the setting of~\textup{(a)} and
 Proposition~\ref{prop:yangian-dk5-spectral-factorization-shifts}.
 If there is a completed vector seed
 \(V^\omega(0)\in \mathcal C_q^\omega\) with
 \(J_q^\omega(V(0))\cong V^\omega(0)\), and \(J_q^\omega\)
 intertwines source shifts with the target pullback family
 \(\mathsf T_a^\omega=\rho_a^*\), then the hypotheses
 of~\textup{(a)} are automatic.

\item\emph{Vector-line realization.}
 Work in the setting of
 Propositions~\ref{prop:yangian-dk5-spectral-vector-line}
 and~\ref{prop:yangian-dk5-spectral-factorization-shifts}.
 If \(J_q^\omega\) restricts to an equivalence
 \(\mathcal L_q^{\mathrm{vec,fd}}
 \xrightarrow{\sim}
 \mathcal L_q^{\mathrm{vec}}\),
 then the hypotheses of~\textup{(a)} are automatic.

\item\emph{Ambient vector-line realization.}
 Assume the hypotheses of
 Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line},
 and let \(\mathcal C_{q,\mathrm{mult}}^\omega\) be the resulting
 multiplicative spectral compact core. Then \(J_q^{\mathrm{mult}}\)
 restricts to an equivalence on the source vector line, and the
 ordered vector packet, completed fundamental packet, ordered
 tensor-generator packet, compact core, and ambient completed spectral
 category
 \(\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}
 \simeq
 \operatorname{Ind}(\mathcal C_{q,\mathrm{mult}}^\omega)\)
 are all formal from that ambient vector-line realization.
\end{enumerate}
\end{corollary}

\begin{proof}
\textup{(a)}
The shifts preserve \(\mathcal{L}^{\mathrm{vec}}_{q}\), so
Proposition~\ref{prop:yangian-dk5-spectral-vector-seed} forces the
vector-line equivalence.
Propositions~\ref{prop:yangian-dk5-spectral-vector-line},
\ref{prop:yangian-dk5-spectral-vector-packet},
\ref{prop:yangian-dk5-spectral-fundamental-packet}, and
\ref{prop:yangian-dk5-spectral-realization-formal}
promote it through the ordered vector packet,
fundamental packet, generator packet, and full compact core.
Corollary~\ref{cor:yangian-dk5-spectral-packet-ind} gives the
ind-completion.

\textup{(b)}
Proposition~\ref{prop:yangian-dk5-spectral-factorization-shifts}
constructs \(\mathsf T_a^\omega=\rho_a^*\) intrinsically; setting
\(V^\omega(a):=\mathsf T_a^\omega(V^\omega(0))\) recovers the
hypotheses of~\textup{(a)}.

\textup{(c)}
Propositions~\ref{prop:quantum-fd-vector-seed-shifts}
and~\ref{prop:yangian-dk5-spectral-seed-shift-construction} construct
and transport the seed-and-shift datum;
Proposition~\ref{prop:yangian-dk5-spectral-core-shifts} extends it to
the compact core. On the multiplicative locus, the target shifts are
intrinsic by
Proposition~\ref{prop:yangian-dk5-spectral-factorization-shifts}.

\textup{(d)}
Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line}
constructs the compact core;~\textup{(c)} gives the sub-packet
formality; Corollary~\ref{cor:yangian-dk5-spectral-packet-ind} gives
the ambient ind-completion.
\end{proof}

\begin{corollary}[Schur-simple ambient seed criterion for the
multiplicative spectral vector line; \ClaimStatusProvedHere]
\label{cor:yangian-dk5-spectral-factorization-schur-seed-line}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}.
Assume that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item there is an isomorphism
 \[
 J_q^{\mathrm{mult}}(V(0))\cong V^{\mathrm{mult}}(0);
 \]
\item the ambient seed is Schur-simple:
 \[
 \End(V^{\mathrm{mult}}(0))\cong \mathbb C;
 \]
\item on the source vector line,
 \(J_q^{\mathrm{mult}}\) intertwines the standard source loop-rotation
 autoequivalences \(\mathsf T_a^{\mathrm{fd}}\) with the ambient
 dilation pullbacks \(\rho_a^*\).
\end{enumerate}
Then the hypotheses of
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}
are automatic. Consequently the restriction of \(J_q^{\mathrm{mult}}\)
to the source vector line is an exact braided-monoidal equivalence
\[
\mathcal L_q^{\mathrm{vec,fd}}
\xrightarrow{\sim}
\mathcal L_q^{\mathrm{vec,mult}}.
\]

\end{corollary}

\begin{proof}
Schur simplicity on both sides
(Lemma~\ref{lem:quantum-fd-vector-seed-schur} and
assumption~\textup{(ii)}) makes the one-object subcategories
equivalent after choosing~\textup{(i)}. Apply
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}.
\end{proof}

\begin{corollary}[One ambient multiplicative vector seed closes the
spectral DK-5 side; \ClaimStatusProvedHere]
\label{cor:yangian-dk5-spectral-factorization-ambient-one-seed}
Assume the hypotheses of
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}.
Let
\[
\mathcal C_{q,\mathrm{mult}}^\omega
\subset
\Factord(\bC^\times;\QGspec(R_{\cA}))
\]
be the smallest full stable idempotent-complete braided-monoidal
subcategory containing the ambient dilation orbit
\(\mathcal L_q^{\mathrm{vec,mult}}\) of \(V^{\mathrm{mult}}(0)\).
Then:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \(\mathcal C_{q,\mathrm{mult}}^\omega\) is exactly the
 multiplicative spectral compact core forced by that single ambient
 vector seed;
\item the completed vector line, ordered vector packet, completed
 fundamental packet, ordered tensor-generator packet, compact core,
 and ambient completed spectral category are all formal from that
 seed.
\end{enumerate}

\end{corollary}

\begin{proof}
Apply
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}
to verify the hypotheses of
Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line},
then
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-vector-line}.
\end{proof}

\begin{corollary}[One Schur-simple ambient multiplicative vector seed
closes the spectral DK-5 side; \ClaimStatusProvedHere]
\label{cor:yangian-dk5-spectral-factorization-ambient-schur-seed}
Work in the setting of
Corollary~\ref{cor:yangian-dk5-spectral-factorization-schur-seed-line}.
Let
\[
\mathcal C_{q,\mathrm{mult}}^\omega
\subset
\Factord(\bC^\times;\QGspec(R_{\cA}))
\]
be the smallest full stable idempotent-complete braided-monoidal
subcategory containing the ambient dilation orbit
\(\mathcal L_q^{\mathrm{vec,mult}}\) of \(V^{\mathrm{mult}}(0)\).
Then the completed vector line, ordered vector packet, completed
fundamental packet, ordered tensor-generator packet, compact core, and
ambient completed spectral category are all formal from that single
Schur-simple ambient vector seed.

\end{corollary}

\begin{proof}
Corollary~\ref{cor:yangian-dk5-spectral-factorization-schur-seed-line}
supplies the hypotheses of
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-one-seed}.
\end{proof}

\begin{theorem}[Spectral DK-5 seed-pair reduction hierarchy;
\ClaimStatusProvedHere]
\label{thm:yangian-dk5-spectral-factorization-seed-mono}%
\label{thm:yangian-dk5-spectral-factorization-seed-mono}%
\label{thm:yangian-dk5-spectral-factorization-seed-trig}%
\label{thm:yangian-dk5-spectral-factorization-seed-trig}%
\label{thm:yangian-dk5-spectral-factorization-seed-channels}%
\label{thm:yangian-dk5-spectral-factorization-seed-single-line}%
\label{thm:yangian-dk5-spectral-factorization-seed-exchange}%
\label{thm:yangian-dk5-spectral-factorization-seed-exchange-mult}%
\label{thm:yangian-dk5-spectral-factorization-seed-alt-mult}%
Work in the setting of
Definitions~\ref{def:ordered-e1-factorization}
and~\ref{def:spectral-quantum-group}. Fix one ambient object
\(V^{\mathrm{mult}}(0)\in \Factord(\bC^\times;\QGspec(R_{\cA}))\)
and define its dilation orbit by
\(V^{\mathrm{mult}}(a):=\rho_a^*V^{\mathrm{mult}}(0)\).
For \(a,b\in\mathbb C\), write
\(\mathsf B_{a,b}^{\mathrm{mult}}\) for the ambient two-point braid
monodromy operator and \(\mathsf B_{a,b}^{\mathrm{fd}}\) for the
source two-point trigonometric braid operator on the standard
quantum-loop vector line. Then the following successive reductions
hold.
\begin{enumerate}[label=\textup{(\alph*)}]
\item\emph{Monodromy from seed pair.}
 After the canonical identification
 \(V^{\mathrm{mult}}(a)\boxtimes V^{\mathrm{mult}}(b)
 \cong \rho_a^*(V^{\mathrm{mult}}(0)\boxtimes V^{\mathrm{mult}}(b-a))\),
 one has
 \(\mathsf B_{a,b}^{\mathrm{mult}}
 \cong \rho_a^*(\mathsf B_{0,b-a}^{\mathrm{mult}})\).
 On every ordered tensor product, the full braid-group action is
 generated by the one-parameter family
 \(\{\mathsf B_{0,c}^{\mathrm{mult}}\}_{c\in\mathbb C}\) via
 dilation pullbacks. After the Schur-simple ambient seed, the only
 remaining local geometric datum is that seed-pair monodromy family.

\item\emph{Trigonometric identity.}
 The braid-group action on the ambient vector packet agrees with the
 standard source trigonometric action if and only if
 \(\mathsf B_{0,c}^{\mathrm{mult}} \cong
 \mathsf B_{0,c}^{\mathrm{fd}}\) for every \(c\in\mathbb C\).

\item\emph{Channel decomposition.}
 Assume further that for every \(c\), both
 \(\mathsf B_{0,c}^{\mathrm{fd}}\) and
 \(\mathsf B_{0,c}^{\mathrm{mult}}\) intertwine the diagonal
 \(\mathfrak{sl}_M\)-action on \(V\otimes V\). Then the
 trigonometric seed-pair identity holds if and only if the two
 operators act by the same scalar on \(\operatorname{Sym}^2(V)\) and
 on \(\Lambda^2(V)\); equivalently, it is enough to check on
 \(e_1\otimes e_1\) and \(e_1\otimes e_2-e_2\otimes e_1\).

\item\emph{Mixed-tensor reduction.}
 Assume \(M\ge 2\) and that for every \(c\) the source and ambient
 operators agree on the highest-weight line
 (\(\mathsf B_{0,c}^{\mathrm{mult}}(e_1\otimes e_1)
 = \mathsf B_{0,c}^{\mathrm{fd}}(e_1\otimes e_1)\)).
 Then the trigonometric identity holds if and only if the single
 mixed-tensor identity
 \(\mathsf B_{0,c}^{\mathrm{mult}}(e_1\otimes e_2)
 = \mathsf B_{0,c}^{\mathrm{fd}}(e_1\otimes e_2)\) holds.

\item\emph{Exchange coefficient.}
 Under the hypotheses of~\textup{(d)}, write
 \(\mathsf B_{0,c}^{\bullet}(e_1\otimes e_2)
 = \alpha^{\bullet}(c)\,e_1\otimes e_2
 + \beta^{\bullet}(c)\,e_2\otimes e_1\)
 for \(\bullet\in\{\mathrm{fd},\mathrm{mult}\}\).
 Then the trigonometric identity is equivalent to the single scalar
 identity \(\beta^{\mathrm{mult}}(c)=\beta^{\mathrm{fd}}(c)\).
 Both families are \(2\pi i\)-periodic, hence descend to functions
 \(\beta_\times^{\mathrm{fd}},\beta_\times^{\mathrm{mult}}\) of the
 multiplicative ratio \(e^c\), and the identity becomes
 \(\beta_\times^{\mathrm{mult}}=\beta_\times^{\mathrm{fd}}\).

\item\emph{Antisymmetric-channel character.}
 Under the hypotheses of~\textup{(e)}, there exist unique scalar
 functions
 \(\lambda_{\mathrm{alt},\times}^{\mathrm{fd}},
 \lambda_{\mathrm{alt},\times}^{\mathrm{mult}}\) of the
 multiplicative spectral ratio such that
 \(\mathsf B_{0,c}^{\bullet}(e_1\otimes e_2-e_2\otimes e_1)
 = \lambda_{\mathrm{alt},\times}^{\bullet}(e^c)
 (e_1\otimes e_2-e_2\otimes e_1)\).
 The trigonometric seed-pair identity is equivalent to
 \(\lambda_{\mathrm{alt},\times}^{\mathrm{mult}}
 = \lambda_{\mathrm{alt},\times}^{\mathrm{fd}}\).
\end{enumerate}
\end{theorem}

\begin{proof}
\textup{(a)}
Functoriality of \(\rho_a^*\) transports
\(\mathsf B_{0,b-a}^{\mathrm{mult}}\) to
\(\mathsf B_{a,b}^{\mathrm{mult}}\).
\(B_n\) is generated by adjacent transpositions, and each adjacent
operator is obtained from the seed-pair family by dilation pullback.
The Schur-simple reduction follows from
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-schur-seed}.

\textup{(b)}
The source braid-group action is generated by
\(\{\mathsf B_{0,c}^{\mathrm{fd}}\}\) via the same dilation argument
(using \(\mathsf T_a^{\mathrm{fd}}\) in place of \(\rho_a^*\)).
Since both sides are generated by their respective seed-pair families,
the full actions agree if and only if the seed-pair families agree.

\textup{(c)}
Diagonal \(\mathfrak{sl}_M\)-equivariance forces both operators to
preserve
\(V\otimes V\cong \operatorname{Sym}^2(V)\oplus \Lambda^2(V)\).
Schur's lemma reduces the comparison to two channel scalars, detected
by the highest-weight generators.

\textup{(d)}
The highest-weight normalization forces
\(\lambda_{\mathrm{sym}}^{\mathrm{mult}}(c)=
\lambda_{\mathrm{sym}}^{\mathrm{fd}}(c)\).
Writing \(e_1\otimes e_2=\frac12(s+a)\) with
\(s\in\operatorname{Sym}^2(V)\), \(a\in\Lambda^2(V)\), the
mixed-tensor identity and linear independence of \(e_1\otimes e_2\)
and \(e_2\otimes e_1\) force the antisymmetric channel scalar to
agree as well, giving~\textup{(c)}.

\textup{(e)}
Under the common symmetric channel scalar, the exchange coefficient
satisfies
\(\beta(c)=(\lambda_{\mathrm{sym}}(c)-\lambda_{\mathrm{alt}}(c))/2\),
so \(\beta^{\mathrm{mult}}=\beta^{\mathrm{fd}}\) is equivalent to
equality of channel scalars and hence of full mixed-tensor outputs.
Both families are \(2\pi i\)-periodic (\(V(c+2\pi i)\cong V(c)\) on
the source, \(\rho_{c+2\pi i}=\rho_c\) on the ambient side), hence
descend to the multiplicative ratio.

\textup{(f)}
The antisymmetric channel scalars are likewise \(2\pi i\)-periodic,
hence descend to multiplicative-ratio functions. Under highest-weight
normalization, equality of exchange coefficients is equivalent to
equality of these antisymmetric-channel characters.
\end{proof}

\begin{corollary}[On the realized spectral packet locus, the ambient
spectral category is the ind-completion of the spectral compact core;
\ClaimStatusProvedHere]
\label{cor:yangian-dk5-spectral-packet-ind}
Assume the hypotheses of
Proposition~\ref{prop:yangian-dk5-spectral-realization-formal}. On
this realized packet locus, define the ambient completed spectral
category by
\[
\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}
:=
\operatorname{Ind}(\mathcal{C}_q^\omega).
\]
Then
\(\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}\)
is presentable, stable, and compactly generated, and its compact
objects are exactly \(\mathcal{C}_q^\omega\). Equivalently, there is a
canonical exact colimit-preserving equivalence
\[
\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}
\xrightarrow{\sim}
\operatorname{Ind}(\mathcal{C}_q^\omega).
\]
In particular, the ambient completed spectral category is compactly
generated by the completed fundamental spectral packet
\(\mathcal{G}^{\mathrm{fund}}_{q}\).
\end{corollary}

\begin{proof}
This is the standard ind-completion package for a small stable
idempotent-complete category: by definition
\(\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}
= \operatorname{Ind}(\mathcal{C}_q^\omega)\), and the resulting
category is presentable, stable, and compactly generated with compact
objects exactly \(\mathcal{C}_q^\omega\) by the standard universal
properties of ind-completion for small stable idempotent-complete
categories \textup{(}Lurie, \emph{HTT}, \S5.3.5, \S5.5.7\textup{)}.
\end{proof}

\begin{proposition}[Canonical completed dg fundamental packet from the
theorematic finite RTT quotients; \ClaimStatusProvedHere]
\label{prop:yangian-dg-fundamental-packet-realization}
Assume the data and hypotheses \textup{(i)}--\textup{(vii)} of
Proposition~\ref{prop:yangian-typea-realization-criterion}. Let
\[
\mathcal{G}^{\mathrm{fund,fd}}_{Y}
\subset
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\]
be the full subcategory generated by finite ordered tensor products of
fundamental evaluation objects. For
\(M\in\mathcal{G}^{\mathrm{fund,fd}}_{Y}\), let \(M_{\le N}\) be its
standard finite-stage evaluation image over \(Y_{\le N}\) under the
compatible quotient comparison of
assumption~\textup{(vi)}. Then the tower \(\{M_{\le N}\}_N\) defines a
continuous completed dg module
\[
J_{Y,\mathrm{pkt}}^\omega(M)
:=
\varprojlim_N M_{\le N}
\]
over \(\Ydg_{\cA}\), and these assignments assemble into a canonical
exact braided monoidal functor
\[
J_{Y,\mathrm{pkt}}^\omega\colon
\mathcal{G}^{\mathrm{fund,fd}}_{Y}
\longrightarrow
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA}).
\]
Let \(\mathcal{G}^{\mathrm{fund}}_{Y}\) denote its essential image.
Then \(J_{Y,\mathrm{pkt}}^\omega\) is an exact braided monoidal
equivalence
\[
\mathcal{G}^{\mathrm{fund,fd}}_{Y}
\xrightarrow{\sim}
\mathcal{G}^{\mathrm{fund}}_{Y}.
\]

\end{proposition}

\begin{proof}
Assumption~\textup{(vi)} identifies each finite quotient with
\(Y_{\le N}\) compatibly with evaluation modules. The inverse limit
\(\varprojlim_N M_{\le N}\) is then a continuous module over
\(\Ydg_{\cA}\) by assumption~\textup{(v)}. Exactness and braided
monoidality are checked stagewise using
assumptions~\textup{(i)}--\textup{(iv)} and~\textup{(vi)}.
\end{proof}

\begin{proposition}[Canonical exact braided-monoidal extension of the
dg packet; \ClaimStatusProvedHere]
\label{prop:yangian-dk5-dg-extension-existence}
Assume the hypotheses of
Proposition~\ref{prop:yangian-dg-fundamental-packet-realization}. Let
\[
\mathcal{C}_Y^\omega
:=
\operatorname{thick}^{\mathrm{idemp}}
\bigl(\mathcal{G}^{\mathrm{fund}}_{Y}\bigr)
\subset
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA}).
\]
Then the packet functor \(J_{Y,\mathrm{pkt}}^\omega\) extends to an
exact braided monoidal functor
\[
J_Y^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\longrightarrow
\mathcal{C}_Y^\omega
\]
whose restriction to \(\mathcal{G}^{\mathrm{fund,fd}}_{Y}\) is
\(J_{Y,\mathrm{pkt}}^\omega\). This extension is unique up to unique
natural isomorphism.

\end{proposition}

\begin{proof}
The stable idempotent-complete braided monoidal target
\(\mathcal{C}_Y^\omega\) allows unique thick-closure extension of
\(J_{Y,\mathrm{pkt}}^\omega\) from
\(\mathcal{G}^{\mathrm{fund,fd}}_{Y}\) to the full source
(Lemma~\ref{lem:yangian-fd-fundamental-generation}). Uniqueness
follows as in
Proposition~\ref{prop:yangian-dk3-generated-core}.
\end{proof}

\begin{proposition}[dg compact-core realization is formal from
extension of the completed fundamental packet;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-dg-realization-formal}
Assume the hypotheses of
Proposition~\ref{prop:yangian-dk5-dg-extension-existence}. Let
\[
\mathcal{C}_Y^\omega
:=
\operatorname{thick}^{\mathrm{idemp}}
\bigl(\mathcal{G}^{\mathrm{fund}}_{Y}\bigr)
\subset
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA}).
\]
Then \(J_Y^\omega\) is an exact braided monoidal equivalence.

\end{proposition}

\begin{proof}
Since \(J_Y^\omega\) is exact braided monoidal and an equivalence on
\(\mathcal{G}^{\mathrm{fund,fd}}_{Y}\), the thick-closure argument of
Proposition~\ref{prop:yangian-dk5-spectral-realization-formal} upgrades
it to an equivalence on the full closures
(Lemma~\ref{lem:yangian-fd-fundamental-generation}).
\end{proof}

\begin{corollary}[Compact generation of the completed dg module
category identifies the ambient dg side with the ind-completion of the
dg compact core;
\ClaimStatusProvedHere]
\label{cor:yangian-dk5-dg-packet-ind}
Assume the hypotheses of
Proposition~\ref{prop:yangian-dk5-dg-realization-formal}. On this
realized packet locus, define the ambient completed dg module category
by
\[
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
:=
\operatorname{Ind}(\mathcal{C}_Y^\omega).
\]
Then \(\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})\) is presentable,
stable, and compactly generated, and its compact objects are exactly
\(\mathcal{C}_Y^\omega\). Equivalently, there is a canonical exact
colimit-preserving equivalence
\[
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\xrightarrow{\sim}
\operatorname{Ind}(\mathcal{C}_Y^\omega).
\]
In particular, \(\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})\) is
compactly generated by the completed fundamental dg-shifted packet
\(\mathcal{G}^{\mathrm{fund}}_{Y}\).

\end{corollary}

\begin{proof}
This is again the standard ind-completion package for a small stable
idempotent-complete category: by definition
\(\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
= \operatorname{Ind}(\mathcal{C}_Y^\omega)\), and the resulting
category is presentable, stable, and compactly generated with compact
objects exactly \(\mathcal{C}_Y^\omega\) by the standard universal
properties of ind-completion for small stable idempotent-complete
categories \textup{(}Lurie, \emph{HTT}, \S5.3.5, \S5.5.7\textup{)}.
\end{proof}

\begin{corollary}[Given dg compact-core realization, the remaining
DK-5 input is spectral vector seed-and-shift realization;
\ClaimStatusProvedHere]
\label{cor:yangian-dk5-dg-half-only}
Assume the hypotheses of
Corollary~\ref{prop:yangian-typea-dg-local-closure}. Assume further
that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the completed dg-shifted and spectral categories are presentable,
 stable, and compactly generated, with compact objects exactly
 \(\mathcal{C}_Y^\omega\) and \(\mathcal{C}_q^\omega\);
\item the spectral compact core admits an exact braided monoidal
 functor \(J_q^\omega\) whose restriction to the vector evaluation
 line is an equivalence onto the completed vector spectral line, as in
 Proposition~\ref{prop:yangian-dk5-spectral-vector-line}; and
\item there exists an exact braided monoidal equivalence
 \[
 J_Y^\omega\colon
 \operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
 \xrightarrow{\sim}
 \mathcal{C}_Y^\omega
 \]
 identifying the fundamental evaluation objects with the completed
 fundamental dg-shifted packet.
\end{enumerate}
Then the standard type-$A$ Yangian DK-5 packet closes.

\end{corollary}

\begin{proof}
Propositions~\ref{prop:quantum-fd-vector-seed-shifts},
\ref{prop:yangian-dk5-spectral-seed-shift-construction},
and~\ref{prop:yangian-dk5-spectral-core-shifts} transport the standard
seed-and-shift datum to the spectral compact core.
Corollary~\ref{cor:yangian-dk5-spectral-seed-realization} closes the
spectral packet. Together with the dg hypotheses,
Corollary~\ref{cor:yangian-dk5-core-realization} closes DK-5.
\end{proof}

\begin{corollary}[DK-5 closes once the compact cores realize a
finite-dimensional factorization DK pair; \ClaimStatusProvedHere]
\label{cor:yangian-dk5-core-realization}
Assume the hypotheses of
Corollary~\ref{prop:yangian-typea-dg-local-closure}. Assume further
that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the completed dg-shifted and spectral categories are presentable,
 stable, and compactly generated, with compact objects exactly
 $\mathcal{C}_Y^\omega$ and $\mathcal{C}_q^\omega$;
\item the compact cores are exact braided monoidal realizations of the
 chosen finite-dimensional factorization DK pair in the sense of
 Proposition~\ref{prop:yangian-dk5-core-realization}.
\end{enumerate}
Then the standard type-$A$ Yangian DK-5 packet closes.

\end{corollary}

\begin{proof}
Apply Proposition~\ref{prop:yangian-dk5-core-realization} for the
compact-core equivalence, then
Proposition~\ref{prop:yangian-dk5-ind-extension} for the ambient
extension.
\end{proof}

\begin{corollary}[Type-\texorpdfstring{$A$}{A} MC4 reduction chain:
 five closure criteria; \ClaimStatusProvedHere]
\label{cor:yangian-typea-mc4-closure-criterion}%
\label{cor:yangian-typea-degree2-plus-generators}%
\label{cor:yangian-typea-casimir-plus-generators}%
\label{cor:yangian-typea-factorization-local-closure}%
\label{cor:yangian-typea-shared-seed-plus-generators}%
Assume the hypotheses of
Propositions~\ref{prop:yangian-dk4-typea-frontier}
and~\ref{prop:yangian-dk5-compact-generators}.
The standard type-$A$ Yangian MC4 packet admits the following
successive reductions.
\begin{enumerate}[label=\textup{(\roman*)}]
\item\emph{Minimal closure.}
 MC4 closes once the dg-shifted or factorization one-factor kernel is
 identified with the standard normalized RTT residue on the
 fundamental evaluation line (under the symmetry and normalization
 hypotheses of
 Proposition~\ref{prop:yangian-dk4-typea-frontier} this is equivalent
 to
 \(
 \Xi_a(e_1\otimes e_2)=-\hbar(e_2\otimes e_1)
 \)), and the compact-generator comparison
 $\mathcal{G}^{\mathrm{fund}}_Y \to \mathcal{G}^{\mathrm{fund}}_q$
 is an equivalence.

\item\emph{One-loop exactness.}
 Assume further the one-loop exactness and seed-normalization
 hypotheses of
 Proposition~\ref{prop:dg-shifted-rtt-degree2-mixed-tensor-criterion}
 and
 Corollary~\ref{prop:dg-shifted-rtt-seed-normalized-coefficient} on
 the standard type-$A$ fundamental line. Then the remaining MC4
 input is the single degree-$2$ coefficient identity
 \[
 r_a^{\mathrm{fund}}(z)(e_1\otimes e_2)
 =
 -\hbar(e_2\otimes e_1),
 \]
 where $r_a^{\mathrm{fund}}(z)$ is induced by
 $r(z)=\tau|_{\deg 2}$ on the ordered fundamental line, together
 with the compact-generator comparison.

\item\emph{Casimir insertion.}
 If in addition the ordered fundamental-line degree-$2$ coefficient is
 the standard trace-zero Casimir insertion
 \[
 r_a^{\mathrm{fund}}(z)\big|_{z_1=z_2}
 =
 -\hbar\,\Omega_{\mathfrak{sl}_M}^{\mathrm{fund}}
 =
 -\hbar\Bigl(P-\frac{1}{M}\id\Bigr),
 \]
 then the local coefficient identity~\textup{(ii)} is automatic, and
 the remaining MC4 input is compact generation plus transport on the
 completed fundamental evaluation packet.

\item\emph{Factorization closure.}
 On the ordered factorization target,
 Corollary~\ref{prop:factorization-fundamental-casimir-identity}
 supplies the Casimir hypothesis of~\textup{(iii)} automatically.
 Hence the remaining MC4 input on the factorization side is compact
 generation plus fundamental-packet transport.

\item\emph{Shared seed closure.}
 Assume the hypotheses of~\textup{(iv)} on the ordered factorization
 target and of
 Corollary~\ref{prop:yangian-typea-dg-local-closure} on an ordered
 dg-shifted target presented by the same ordered bar seed. Then the
 local MC4 packet is automatic on both sides, and the remaining
 standard type-$A$ Yangian MC4 input is exactly the compact-generator
 comparison
 \[
 \mathcal{G}^{\mathrm{fund}}_Y
 \xrightarrow{\sim}
 \mathcal{G}^{\mathrm{fund}}_q.
 \]
\end{enumerate}
\end{corollary}

\begin{proof}
\textup{(i)}
Proposition~\ref{prop:yangian-dk4-typea-frontier} reduces DK-4 to the
mixed-tensor coefficient;
Proposition~\ref{prop:dg-shifted-rtt-degree2-fundamental-casimir}
and Corollary~\ref{prop:factorization-fundamental-casimir-identity}
show the Casimir insertion forces it.
Proposition~\ref{prop:yangian-dk5-compact-generators} reduces DK-5 to
compact generators.

\textup{(ii)}
Corollary~\ref{prop:dg-shifted-rtt-seed-normalized-coefficient}
identifies the residue with the degree-$2$ coefficient. Under
one-loop exactness
(Proposition~\ref{prop:dg-shifted-rtt-degree2-mixed-tensor-criterion}),
this forces the DK-4 content of
Proposition~\ref{prop:yangian-dk4-typea-frontier}. The remaining
DK-5 input is
Corollary~\ref{cor:yangian-dk5-fundamental-packet}.

\textup{(iii)}
Proposition~\ref{prop:dg-shifted-rtt-degree2-fundamental-casimir}
forces \(\beta_a=-1\), which gives the coefficient
identity~\textup{(ii)}.

\textup{(iv)}
Corollary~\ref{prop:factorization-fundamental-casimir-identity}
supplies the Casimir hypothesis of~\textup{(iii)}.

\textup{(v)}
Part~\textup{(iv)} closes the factorization side;
Corollary~\ref{prop:yangian-typea-dg-local-closure} transports via
the shared seed.
Proposition~\ref{prop:yangian-dk5-compact-generators} reduces the
remaining DK-5 packet to compact generators.
\end{proof}

\begin{remark}[Exact extra input for DK-5]
\label{rem:yangian-dk5-input}
After Proposition~\ref{prop:yangian-dk4-typea-frontier}, the remaining
DK-5 packet is the compact-core categorical packet:
\textup{(i)}~on the dg side,
Propositions~\ref{prop:yangian-dg-fundamental-packet-realization},
\ref{prop:yangian-dk5-dg-extension-existence},
and~\ref{prop:yangian-dk5-dg-realization-formal} construct and extend
the canonical dg packet, and
Corollary~\ref{cor:yangian-dk5-dg-packet-ind} removes the remaining
dg obstruction;
\textup{(ii)}~on the spectral side, realize the standard vector
seed-and-shift datum
(Propositions~\ref{prop:quantum-fd-vector-seed-shifts},
\ref{prop:yangian-dk5-spectral-seed-shift-construction},
\ref{prop:yangian-dk5-spectral-core-shifts}); on the multiplicative
locus this contracts to one Schur-simple ambient vector seed
(Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-schur-seed})
and then to one antisymmetric-channel character
(Proposition~\ref{thm:yangian-dk5-spectral-factorization-seed-alt-mult});
\textup{(iii)}~with both compact-core realizations,
Corollary~\ref{cor:yangian-dk5-core-realization} closes DK-5 via
ind-extension (Proposition~\ref{prop:yangian-dk5-ind-extension}).
\end{remark}

\begin{remark}[MC4 boundary for Yangian towers]
\label{rem:yangian-mc4-boundary}
The finite RTT Yangians are theorematic (bar-cobar, $R\mapsto R^{-1}$,
evaluation-locus DK square). The genuine MC4 input is
Hypothesis~\textup{(ii)} of Conjecture~\ref{conj:full-dk-bridge}: the
RTT-adapted realization of the canonical H-level target
(Proposition~\ref{prop:yangian-canonical-hlevel-target}).
The standard RTT tower supplies the completed M-level package
(Corollary~\ref{cor:yangian-standard-mc4-package}), and
Corollary~\ref{cor:yangian-hlevel-comparison-criterion} makes the
comparison formal once one supplies an RTT-adapted dg realization whose
finite RTT quotients recover the theorematic stages and whose completed
bar/cobar comparison data is compatible with the standard RTT tower.
For standard type-$A$,
Proposition~\ref{prop:yangian-dk4-typea-frontier} sharpens DK-4 to
one mixed-tensor residue check, while the remaining DK-5 work is the
compact-core realization and extension packet recorded in
Remark~\ref{rem:yangian-dk5-input}. On the spectral side, the
reduction chain contracts the live input to one antisymmetric-channel
character on the multiplicative spectral line
(Proposition~\ref{thm:yangian-dk5-spectral-factorization-seed-alt-mult}).
MC5 begins only after this H-level comparison packet is in place.
\end{remark}

\begin{remark}[What the Yangian tower still has to prove]
\label{rem:yangian-mc4-checklist}
By Proposition~\ref{prop:mc4-reduction-principle}, the Yangian-tower
completion programme, now resolved by the strong completion-tower theorem (Theorem~\ref{thm:completed-bar-cobar-strong}), originally broke into four checks:
\textup{(1)}~finite RTT truncations in the proved $\Eone$-Koszul regime;
\textup{(2)}~compatible descent of finite-stage bar/cobar
(Proposition~\ref{prop:inverse-limit-differential-continuity});
\textup{(3)}~Mittag--Leffler on
$\{H^m(\bar B(Y_{\le N}))\}_N$
(Corollary~\ref{cor:yangian-weight-cutoff});
\textup{(4)}~inverse-limit identification
(Proposition~\ref{prop:yangian-rtt-completion-identification}).
Items~\textup{(1)}--\textup{(3)} are absorbed by the strong
completion-tower theorem: the finite RTT stages lie in
$\CompCl(\Fft)$, the coefficient-stability criterion
(Theorem~\ref{thm:coefficient-stability-criterion}) gives automatic
Mittag--Leffler, and the reduced-weight windows
(Theorem~\ref{thm:window-locality}) make each finite check
explicit. The Yangian jet principle
\ifannalsedition\else
(Conjecture~\ref{conj:jet-principle})
\fi predicts that reduced-weight-$q$
bar windows determine Yangian jets through order~$z^{-q}$.
For~\textup{(4)},
Corollary~\ref{cor:yangian-hlevel-comparison-criterion} reduces the
H-level comparison to constructing a filtered model whose finite
quotients match the proved stages; in type~$A$,
Proposition~\ref{prop:yangian-dk4-typea-frontier} reduces this to one
residue check, and the dg fundamental packet is already constructed by
Proposition~\ref{prop:yangian-dg-fundamental-packet-realization}.
\end{remark}

\begin{proposition}[Yangian tower criterion from finite RTT stages;
\ClaimStatusProvedHere]
\label{prop:yangian-tower-mc4-criterion}
Let
\[
Y = \varprojlim_N Y_{\le N}
\]
be a separated complete Yangian tower assembled from finite RTT stages.
Assume:
\begin{enumerate}
\item each $Y_{\le N}$ lies in the proved $\Eone$-Koszul regime of this
 chapter;
\item the transition maps $Y_{\le N+1} \to Y_{\le N}$ are compatible
 with the finite-stage bar complexes and bar-cobar
 quasi-isomorphisms;
\item for every cohomological degree~$m$, the inverse system
 $\{H^m(\bar B(Y_{\le N}))\}_N$ is eventually constant; and
\item the transition maps define an inverse system of curved dg
 coalgebras on the finite-stage bar complexes.
\end{enumerate}
Then the completed Yangian bar object
\[
\widehat{\bar B}(Y) := \varprojlim_N \bar B(Y_{\le N})
\]
is a separated complete pro-nilpotent curved dg coalgebra and the
canonical comparison map
\[
\Omega\bigl(\widehat{\bar B}(Y)\bigr) \xrightarrow{\sim} Y
\]
is a quasi-isomorphism. This gives the M-level completed bar-cobar
package for the Yangian tower under the stated inverse-limit
hypotheses. As in the $\mathcal{W}_\infty$ case, the eventual-constancy
hypothesis may be weakened to eventual surjectivity on finite-dimensional
weight slices by Corollary~\ref{cor:mc4-surjective-criterion}.
\end{proposition}

\begin{proof}
Assumption~\textup{(iii)} is exactly the stabilization hypothesis of
Corollary~\ref{cor:mc4-degreewise-stabilization}, and
Assumptions~\textup{(i)}, \textup{(ii)}, and~\textup{(iv)} identify the
Yangian tower with the general inverse-limit setting of
Proposition~\ref{prop:mc4-reduction-principle}, while
Proposition~\ref{prop:inverse-limit-differential-continuity} supplies
the continuity of the completed bar and cobar differentials.
Applying Corollary~\ref{cor:mc4-degreewise-stabilization} to the tower
$\{\bar B(Y_{\le N})\}_N$ yields the stated completed bar-cobar
quasi-isomorphism.
\end{proof}

\begin{remark}[Standard-tower Yangian frontier]
For the standard type-$A$ RTT tower, the finite-stage M-level package
is theorematic, while the remaining live inputs are the H-level
realization and the post-core DK-5 compact/completed comparison.
Type~$A$ does not close MC3 here:
Theorem~\ref{thm:mc3-type-a-resolution} reduces the old four-package
problem to the remaining compact-completion packet
\textup{(}Conjecture~\ref{conj:dk-compacts-completion}\textup{)}.
Across arbitrary type, the all-types categorical CG/core surface is
already proved \textup{(}Corollary~\ref{cor:mc3-all-types}\textup{)};
what remains is the corresponding post-core extension/completion
packet together with the relevant realization input.
\end{remark}

\begin{corollary}[Standard RTT cutoff for Yangian towers;
\ClaimStatusProvedHere]
\label{cor:yangian-weight-cutoff}
Let $Y_{\le N}$ be the standard RTT truncation retaining the generators
$T_{ij}^{(r)}$ with $r \le N$, and let
$Y = \varprojlim_N Y_{\le N}$ be the resulting inverse-limit tower.
Then the tower of bar complexes $\{\bar B(Y_{\le N})\}_N$ satisfies the
hypotheses of Proposition~\ref{prop:mc4-weight-cutoff} for the total
RTT-level filtration. In particular, for every cohomological degree
$m$ and total RTT level $\ell$, the map
\[
H^m(\bar B(Y_{\le N+1}))_\ell \xrightarrow{\sim}
H^m(\bar B(Y_{\le N}))_\ell
\]
is an isomorphism for all $N \ge \ell$.

Therefore the standard RTT tower already supplies the
surjectivity/stabilization part of MC4. Together with
Proposition~\ref{prop:inverse-limit-differential-continuity} and
Proposition~\ref{prop:yangian-rtt-completion-identification}, this
reduces the standard RTT tower to the standard-RTT completed M-level
package of Corollary~\ref{cor:yangian-standard-mc4-package}.
\end{corollary}

\begin{proof}
The RTT generators are graded by level~$r$, and the RTT relation is
homogeneous in the total level (Theorem~\ref{thm:yangian-koszul-dual},
Step~2a). A bar chain of total RTT level $\ell$ can therefore involve
only generators $T_{ij}^{(r)}$ with $r \le \ell$. Once $N \ge \ell$,
all such generators already lie in the truncation $Y_{\le N}$, so the
filtered bar subcomplex of levels $\le \ell$ is identical in every
later stage. Proposition~\ref{prop:mc4-weight-cutoff} then gives the
stated stabilization on cohomology slices.
\end{proof}

\begin{proposition}[Inverse-limit identification of the standard RTT
completion; \ClaimStatusProvedHere]
\label{prop:yangian-rtt-completion-identification}
Let $\widehat Y_{\mathrm{RTT}}$ be the coefficientwise RTT completion:
its elements are formal matrices
\[
T(u)=1+\hbar\sum_{r \ge 0} T^{(r)}u^{-r-1}
\]
satisfying the RTT relation coefficientwise, with topology of
coefficientwise convergence in the modes $T_{ij}^{(r)}$. Then the
canonical truncation maps identify this completed RTT algebra with the
standard inverse-limit tower:
\[
\widehat Y_{\mathrm{RTT}} \xrightarrow{\sim} \varprojlim_N Y_{\le N}.
\]
\end{proposition}

\begin{proof}
For each $N$, truncating the formal matrix after level~$N$ produces
\[
T_{\le N}(u)=1+\hbar\sum_{r=0}^N T^{(r)}u^{-r-1},
\]
which satisfies the finite RTT relations defining $Y_{\le N}$ because
every coefficient of the RTT equation only involves finitely many modes.
This gives compatible algebra maps
$q_N\colon \widehat Y_{\mathrm{RTT}} \to Y_{\le N}$ and hence a map
\[
q\colon \widehat Y_{\mathrm{RTT}} \longrightarrow \varprojlim_N Y_{\le N}.
\]

Conversely, let $(x_N)_N$ be a compatible family in the inverse limit.
Represent $x_N$ by a truncated RTT matrix
$T^{(\le N)}(u)=1+\hbar\sum_{r=0}^N T_N^{(r)}u^{-r-1}$.
Compatibility of the truncation maps implies that for each fixed
$r \ge 0$, the coefficient $T_N^{(r)}$ is independent of $N$ once
$N \ge r$; denote the stable value by $T^{(r)}$. These stable
coefficients assemble into a formal RTT matrix
\[
T(u)=1+\hbar\sum_{r \ge 0} T^{(r)}u^{-r-1}.
\]
To verify the RTT relation coefficientwise, fix a coefficient of
$u^{-a-1}v^{-b-1}$. That coefficient depends only on modes
$T^{(r)}$ with $r \le \max\{a,b\}+1$, so it is already visible in every
finite truncation $Y_{\le N}$ with $N \ge \max\{a,b\}+1$. Since each
$T^{(\le N)}(u)$ satisfies the finite RTT relation, the chosen
coefficient vanishes in the limit. Thus $T(u)$ lies in
$\widehat Y_{\mathrm{RTT}}$.

The constructions are inverse to one another: truncating the recovered
formal RTT matrix returns the original compatible family, and taking the
stable coefficients of a formal RTT matrix recovers it exactly. Hence
$q$ is an isomorphism.
\end{proof}

\begin{corollary}[Standard RTT tower satisfies the M-level MC4 package;
\ClaimStatusProvedHere]
\label{cor:yangian-standard-mc4-package}
For the standard RTT truncation tower, the completed bar object
\[
\widehat{\bar B}(Y) := \varprojlim_N \bar B(Y_{\le N})
\]
has continuous bar and cobar differentials, and the canonical
comparison map
\[
\Omega\bigl(\widehat{\bar B}(Y)\bigr) \xrightarrow{\sim}
\widehat Y_{\mathrm{RTT}}
\]
is a quasi-isomorphism.
Thus the standard RTT tower supplies the full M-level completed
bar-cobar package for the coefficientwise RTT completion. What remains
open is the H-level comparison of $\widehat Y_{\mathrm{RTT}}$ with the
dg-shifted Yangian or factorization-theoretic completion.
\end{corollary}

\begin{proof}
The finite RTT stages lie in the proved $\Eone$-Koszul regime, so the
finite-stage bar-cobar quasi-isomorphisms are already available.
Proposition~\ref{prop:inverse-limit-differential-continuity} supplies
continuity of the completed bar and cobar differentials, and
Corollary~\ref{cor:yangian-weight-cutoff} supplies the
Mittag--Leffler/stabilization input for the standard RTT tower.
Applying Proposition~\ref{prop:mc4-reduction-principle} to that tower
and identifying the target inverse limit by
Proposition~\ref{prop:yangian-rtt-completion-identification} gives the
stated quasi-isomorphism.
\end{proof}

\begin{corollary}[H-level comparison criterion for dg-shifted Yangians;
\ClaimStatusProvedHere]
\label{cor:yangian-hlevel-comparison-criterion}
Let $\Ydg_{\cA}$ be a separated complete dg algebra equipped with a
descending RTT-level filtration by closed dg ideals. Assume:
\begin{enumerate}
\item $\Ydg_{\cA}$ is the inverse limit of its finite RTT-level
 quotients;
\item for each $N$ there is a dg algebra quasi-isomorphism
 \[
 \Ydg_{\cA}/F^{N+1}\Ydg_{\cA} \xrightarrow{\sim} Y_{\le N}
 \]
 compatible with the truncation tower; and
\item the quotient tower inherits bar-cobar comparison maps compatible
 with the standard RTT tower and has continuous completed bar and cobar
 differentials.
\end{enumerate}
Then the induced comparison map
\[
\Ydg_{\cA} \xrightarrow{\sim} \widehat Y_{\mathrm{RTT}}
\]
is a quasi-isomorphism, and $\Ydg_{\cA}$ defines the same completed
M-level bar-cobar object as the standard RTT completion. Thus the
remaining Yangian H-level problem is to identify the canonical
formal-moduli target of
Proposition~\ref{prop:yangian-canonical-hlevel-target}, or any chosen
equivalent dg model, with a filtered dg-shifted or factorization model
with theorematic finite RTT quotients. The MC4 structural
framework is proved (Theorem~\ref{thm:completed-bar-cobar-strong});
the finite RTT stages lie in $\CompCl(\Fft)$ and the
coefficient-stability criterion
(Theorem~\ref{thm:coefficient-stability-criterion}) reduces
convergence to window stabilization. Once such an RTT-adapted
realization is supplied, the remaining coefficient
comparison is the exact packet
\[
\mathsf{K}^{\mathrm{line}}_{a,b}(N)
=\mathsf{K}^{\mathrm{RTT}}_{a,b}(N)
\qquad (0\le a,b\le N),
\]
detected on the boundary strip
$\{\Delta_{a,0}(N)\}_{0\le a\le N}$, not another local RTT
calculation.
\end{corollary}

\begin{proof}
Apply Proposition~\ref{prop:completed-target-comparison} with
$\cA_{\le N}=Y_{\le N}$. Since the finite RTT truncation maps are
surjective and the quotients of $\Ydg_{\cA}$ are quasi-isomorphic to
them, the Mittag--Leffler input required there is automatic on
cohomology. The bar-cobar statement then follows from the final part
of Proposition~\ref{prop:completed-target-comparison}, together with
Corollary~\ref{cor:yangian-standard-mc4-package}.
\end{proof}

\begin{remark}[Application to the H-level identification frontier]
\label{rem:yangian-hlevel-comparison-criterion-application}
Corollary~\ref{cor:yangian-hlevel-comparison-criterion} is the proved
Yangian half of the frontier conjecture
\ifannalsedition\else
(Conjecture~\ref{conj:master-infinite-generator})
\fi: the remaining step is to supply an RTT-adapted realization of the
canonical H-level target and verify the boundary-strip coefficient
packet.
\end{remark}

\begin{proposition}[Standard type-\texorpdfstring{$A$}{A} realization criterion from shared
bar seed and finite RTT quotients; \ClaimStatusProvedHere]
\label{prop:yangian-typea-realization-criterion}
Let $\Ydg_{\cA}$ be a separated complete dg algebra equipped with:
\begin{enumerate}[label=\textup{(\roman*)}]
\item a translation operator;
\item a Maurer--Cartan element $r(z)$;
\item a twisted coproduct; and
\item a descending RTT-level filtration by closed dg ideals
 \[
 F^1\Ydg_{\cA} \supset F^2\Ydg_{\cA} \supset \cdots
 \]
 preserved by all three structures above.
\end{enumerate}
Assume further that:
\begin{enumerate}[label=\textup{(\roman*)},resume]
\item $\Ydg_{\cA}\cong \varprojlim_N \Ydg_{\cA}/F^{N+1}\Ydg_{\cA}$;
\item for every $N$ there is a dg algebra quasi-isomorphism
 \[
 \Ydg_{\cA}/F^{N+1}\Ydg_{\cA}\xrightarrow{\sim}Y_{\le N}
 \]
 compatible with the RTT truncation tower, standard evaluation
 modules, and the induced degree-$2$ twisting morphism;
\item the quotient tower inherits bar-cobar comparison maps compatible
 with the standard RTT tower and has continuous completed bar and
 cobar differentials; and
\item on the ordered fundamental evaluation line, the degree-$2$
 coefficient is induced by the same ordered bar twisting morphism as
 on the factorization target, in the sense of
 Proposition~\ref{prop:dg-shifted-factorization-shared-seed}.
\end{enumerate}
Then:
\begin{enumerate}[label=\textup{(\alph*)}]
\item the filtration on $\Ydg_{\cA}$ is RTT-adapted in the sense of
 Definition~\ref{def:rtt-adapted-filtration};
\item the induced comparison map
 \[
 \Ydg_{\cA}\xrightarrow{\sim}\widehat Y_{\mathrm{RTT}}
 \]
 is a quasi-isomorphism, so $\Ydg_{\cA}$ realizes the H-level
 dg-shifted Yangian target for the standard type-$A$ tower; and
\item the local standard type-$A$ DK-4 packet is already closed, so the
 only remaining Yangian input is the already-isolated spectral
 vector-line realization package; on the multiplicative spectral
 realization locus this is equivalently the standard spectral vector
 seed-and-shift datum.
\end{enumerate}
\end{proposition}

\begin{proof}
Assumptions~\textup{(v)}--\textup{(vii)} are exactly the hypotheses of
Corollary~\ref{cor:yangian-hlevel-comparison-criterion}. Therefore the
comparison map
\[
\Ydg_{\cA}\xrightarrow{\sim}\widehat Y_{\mathrm{RTT}}
\]
is a quasi-isomorphism, proving~\textup{(b)}. Since
assumptions~\textup{(i)}--\textup{(vii)} are precisely the data
required in Definition~\ref{def:rtt-adapted-filtration}, this also
proves~\textup{(a)}.

Assumption~\textup{(viii)} is the shared-seed hypothesis of
Proposition~\ref{prop:dg-shifted-factorization-shared-seed}, so the
ordered fundamental degree-$2$ coefficient on the dg-shifted target is
the standard trace-zero Casimir insertion. Corollary~\ref{prop:yangian-typea-dg-local-closure}
then closes the local dg-shifted packet on the standard type-$A$
tower. Thus only the DK-5 categorical packet on the completed
fundamental evaluation modules remains. By
Proposition~\ref{prop:yangian-dg-fundamental-packet-realization},
Proposition~\ref{prop:yangian-dk5-dg-realization-formal}, and
Corollary~\ref{cor:yangian-dk5-dg-packet-ind}, the dg side is already
formal from the canonical completed dg packet and its ind-completion.
Thus the only remaining categorical input is the already-isolated
spectral vector-line realization package; on the multiplicative
spectral realization locus this is equivalently the realization of the
standard spectral vector seed-and-shift datum.
This proves~\textup{(c)}.
\end{proof}

\begin{theorem}[Standard type-\texorpdfstring{$A$}{A} Yangian DK-4/DK-5 closure:
seven variant hypotheses; \ClaimStatusProvedHere]
\label{thm:yangian-dk45-closure-variants}%
\label{thm:yangian-typea-realization-plus-compacts}%
\label{thm:yangian-typea-realization-plus-fundamental-packet}%
\label{thm:yangian-typea-realization-plus-core-realization}%
\label{thm:yangian-formal-moduli-plus-core-realization}%
\label{thm:yangian-typea-realization-plus-dg-packet}%
\label{thm:yangian-canonical-realization-plus-one-seed}%
\label{thm:yangian-canonical-realization-plus-vector-line}%
Under any one of the following seven sets of hypotheses, the standard
type-$A$ Yangian DK-4/DK-5 packet closes.
\begin{enumerate}[label=\textup{(\roman*)}]
\item\emph{Realization $+$ compact core.}
 Assume the hypotheses of
 Proposition~\ref{prop:yangian-typea-realization-criterion}. Assume
 further that the compact cores of
 \(\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})\) and
 \(\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}\)
 are presentable, stable, compactly generated, and exactly equivalent
 in a way compatible with DK-3 on the completed fundamental packet.

\item\emph{Realization $+$ completed fundamental packet.}
 Assume the hypotheses of
 Proposition~\ref{prop:yangian-typea-realization-criterion}. Assume
 further that the completed dg-shifted and spectral categories are
 presentable, stable, and compactly generated; that their compact
 objects are the smallest full stable idempotent-complete braided
 monoidal subcategories containing the completed fundamental
 evaluation packets; and that there exist exact braided monoidal
 functors between those compact cores whose restrictions to the
 completed fundamental evaluation packets recover the DK-3 transport
 and whose composites are the identity on that packet.

\item\emph{Realization $+$ core realization.}
 Assume the hypotheses of
 Proposition~\ref{prop:yangian-typea-realization-criterion}. Assume
 further that the completed dg-shifted and spectral categories are
 presentable, stable, and compactly generated, with compact objects
 exactly $\mathcal{C}_Y^\omega$ and $\mathcal{C}_q^\omega$; and that
 those compact cores are exact braided monoidal realizations of the
 chosen finite-dimensional factorization DK pair in the sense of
 Proposition~\ref{prop:yangian-dk5-core-realization}.

\item\emph{Canonical formal-moduli target $+$ core realization.}
 Let $\cA=\mathcal{Y}(\mathfrak{sl}_M)$,
 $\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA}$ be the canonical
 H-level dg target of
 Proposition~\ref{prop:yangian-canonical-hlevel-target}, and let
 $U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ be the canonical associative
 dg model of Proposition~\ref{prop:yangian-canonical-envelope}.
 Assume that the hypotheses of
 Proposition~\ref{prop:yangian-typea-realization-criterion} hold for
 $U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$. Assume further that the
 completed dg-shifted and spectral categories are presentable, stable,
 and compactly generated, with compact objects exactly
 $\mathcal{C}_{\mathfrak g}^\omega$ and $\mathcal{C}_q^\omega$; and
 that those compact cores are exact braided monoidal realizations of
 a chosen finite-dimensional factorization DK pair in the sense of
 Proposition~\ref{prop:yangian-dk5-core-realization}.

\item\emph{Realization $+$ spectral vector-line realization.}
 Assume the hypotheses of
 Proposition~\ref{prop:yangian-typea-realization-criterion}. Assume
 further that the spectral compact core admits an exact braided
 monoidal functor $J_q^\omega$ whose restriction to the vector
 evaluation line is an equivalence onto the completed vector spectral
 line, as in
 Proposition~\ref{prop:yangian-dk5-spectral-vector-line}.

\item\emph{Canonical target $+$ one canonical spectral seed
 (equivariant multiplicative locus).}
 As in~\textup{(iv)}, let $\cA=\mathcal{Y}(\mathfrak{sl}_M)$ with
 canonical target
 $U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ satisfying the hypotheses of
 Proposition~\ref{prop:yangian-typea-realization-criterion}. Assume
 further the equivariant multiplicative spectral realization
 hypotheses of
 Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed},
 so that the shift family is intrinsic and the single canonical
 spectral seed $V^\omega(0):=J_q^\omega(V(0))$ is defined.

\item\emph{Canonical target $+$ spectral vector-line realization.}
 As in~\textup{(iv)}, let $\cA=\mathcal{Y}(\mathfrak{sl}_M)$ with
 canonical target
 $U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ satisfying the hypotheses of
 Proposition~\ref{prop:yangian-typea-realization-criterion}. Assume
 further that the spectral compact core admits an exact braided
 monoidal functor
 \(J_q^\omega\colon
 \operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
 \longrightarrow \mathcal C_q^\omega\)
 whose restriction to the vector evaluation line is an equivalence
 onto the completed vector spectral line, as in
 Proposition~\ref{prop:yangian-dk5-spectral-vector-line}.
\end{enumerate}
\end{theorem}

\begin{proof}
In each variant, Proposition~\ref{prop:yangian-typea-realization-criterion}
(applied directly or via its canonical specialization) closes the local
DK-4 packet on the standard type-$A$ tower.

\textup{(i)}
The compact-core equivalence is the input of
Corollary~\ref{cor:yangian-dk5-compact-core}, which closes DK-5.

\textup{(ii)}
The three additional hypotheses are the input of
Corollary~\ref{cor:yangian-dk5-fundamental-packet}, which closes DK-5.

\textup{(iii)}
The compact-core realization is the input of
Corollary~\ref{cor:yangian-dk5-core-realization}, which closes DK-5.

\textup{(iv)}
Proposition~\ref{prop:yangian-canonical-envelope} identifies the dg
model with the canonical formal-moduli target. The compact-core
hypotheses reduce to variant~\textup{(iii)} with
$\mathcal{C}_Y^\omega$ realized inside
$\operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ as
$\mathcal{C}_{\mathfrak g}^\omega$.

\textup{(v)}
Propositions~\ref{prop:yangian-dk5-dg-extension-existence},
\ref{prop:yangian-dk5-dg-realization-formal}, and
Corollary~\ref{cor:yangian-dk5-dg-packet-ind} close the dg side.
On the spectral side, the vector-line hypothesis, together with
the seed-and-shift construction
(Propositions~\ref{prop:yangian-dk5-spectral-seed-shift-construction}
and~\ref{prop:yangian-dk5-spectral-core-shifts},
Corollary~\ref{cor:yangian-dk5-spectral-seed-realization}), satisfies
the input of Corollary~\ref{cor:yangian-dk5-core-realization}, so
DK-5 closes.

\textup{(vi)}
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed}
makes the hypotheses of
Corollary~\ref{cor:yangian-dk5-spectral-one-seed} automatic. The
completed vector line, fundamental packet, spectral compact core, and
ambient spectral category are all formal, so
variant~\textup{(vii)} is satisfied.

\textup{(vii)}
The vector-line hypothesis is the remaining spectral input of
variant~\textup{(v)} specialized to the canonical target.
\end{proof}

%% ================================================================
%% The seven individual corollaries below are consolidated into
%% Theorem~\ref{thm:yangian-dk45-closure-variants} above.
%% They are retained for reference and for the detailed proofs.
%% ================================================================
\iffalse
\begin{corollary}[Standard type-\texorpdfstring{$A$}{A} DK-4/DK-5 closure from realization
and compact core; \ClaimStatusProvedHere]
\label{cor:yangian-typea-realization-plus-compacts-orig}
Assume the hypotheses of
Proposition~\ref{prop:yangian-typea-realization-criterion}. Assume
further that the compact cores of
\[
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\qquad\text{and}\qquad
\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}
\]
are presentable, stable, compactly generated, and exactly equivalent in
a way compatible with DK-3 on the completed fundamental packet. Then
the standard type-$A$ Yangian DK-4/DK-5 packet closes.

Equivalently, once the H-level dg-shifted realization is constructed on
the shared-bar-seed finite-quotient locus, the only remaining step is
the compact-core equivalence, and that step closes DK-5 formally.
\end{corollary}

\begin{proof}
By Proposition~\ref{prop:yangian-typea-realization-criterion}, the
H-level dg-shifted realization exists and the local standard type-$A$
DK-4 packet is already closed. The additional compact-core hypothesis
is exactly the input of
Corollary~\ref{cor:yangian-dk5-compact-core}, which therefore closes
DK-5. This proves the full DK-4/DK-5 claim.
\end{proof}

\begin{corollary}[Standard type-\texorpdfstring{$A$}{A} DK-4/DK-5 closure from realization
and completed fundamental packet; \ClaimStatusProvedHere]
\label{cor:yangian-typea-realization-plus-fundamental-packet-orig}
Assume the hypotheses of
Proposition~\ref{prop:yangian-typea-realization-criterion}. Assume
further that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the completed dg-shifted and spectral categories are presentable,
 stable, and compactly generated;
\item their compact objects are the smallest full stable
 idempotent-complete braided monoidal subcategories containing the
 completed fundamental evaluation packets; and
\item there exist exact braided monoidal functors between those compact
 cores whose restrictions to the completed fundamental evaluation
 packets recover the DK-3 transport and whose composites are the
 identity on that packet.
\end{enumerate}
Then the standard type-$A$ Yangian DK-4/DK-5 packet closes.

Equivalently, once the shared-bar-seed finite-quotient realization
package is in place, the only remaining categorical step is transport
on the completed fundamental evaluation packet; the compact-core
equivalence and the completed comparison functor are then formal.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:yangian-typea-realization-criterion} supplies the
H-level dg-shifted realization and closes the local standard type-$A$
DK-4 packet. The additional hypotheses are exactly the input of
Corollary~\ref{cor:yangian-dk5-fundamental-packet}, which closes DK-5.
\end{proof}

\begin{corollary}[Standard type-\texorpdfstring{$A$}{A} DK-4/DK-5 closure from dg-shifted
realization and compact-core realization of a chosen
finite-dimensional factorization DK pair; \ClaimStatusProvedHere]
\label{cor:yangian-typea-realization-plus-core-realization-orig}
Assume the hypotheses of
Proposition~\ref{prop:yangian-typea-realization-criterion}. Assume
further that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the completed dg-shifted and spectral categories are presentable,
 stable, and compactly generated, with compact objects exactly
 $\mathcal{C}_Y^\omega$ and $\mathcal{C}_q^\omega$; and
\item those compact cores are exact braided monoidal realizations of
 a chosen finite-dimensional factorization DK pair in the sense of
 Proposition~\ref{prop:yangian-dk5-core-realization}.
\end{enumerate}
Then the standard type-$A$ Yangian DK-4/DK-5 packet closes.

Equivalently, once the shared-bar-seed finite-quotient realization
package is in place, the remaining categorical step is to realize the
compact cores as exact braided monoidal completions of a chosen
finite-dimensional factorization DK pair.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:yangian-typea-realization-criterion} supplies the
H-level dg-shifted realization and closes the local standard type-$A$
DK-4 packet. The additional hypotheses are exactly the input of
Corollary~\ref{cor:yangian-dk5-core-realization}, which closes DK-5.
\end{proof}

\begin{corollary}[Canonical formal-moduli Yangian target closes
DK-4/DK-5 once the compact cores realize a chosen finite-dimensional
DK pair; \ClaimStatusProvedHere]
\label{cor:yangian-formal-moduli-plus-core-realization-orig}
Let
\[
\cA=\mathcal{Y}(\mathfrak{sl}_M),
\qquad
\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA}
\]
be the canonical H-level dg target of
Proposition~\ref{prop:yangian-canonical-hlevel-target}, and let
\[
U^{\mathrm{comp}}(\mathfrak{g}_{\cA})
\]
be the canonical associative dg model of
Proposition~\ref{prop:yangian-canonical-envelope}. Assume that the
hypotheses of Proposition~\ref{prop:yangian-typea-realization-criterion}
hold for \(U^{\mathrm{comp}}(\mathfrak{g}_{\cA})\). Assume further
that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the completed dg-shifted and spectral categories are presentable,
 stable, and compactly generated, with compact objects exactly
 $\mathcal{C}_{\mathfrak g}^\omega$ and $\mathcal{C}_q^\omega$; and
\item those compact cores are exact braided monoidal realizations of
 a chosen finite-dimensional factorization DK pair in the sense of
 Proposition~\ref{prop:yangian-dk5-core-realization}.
\end{enumerate}
Then the standard type-$A$ Yangian DK-4/DK-5 packet closes.

Equivalently, the canonical formal-moduli target already exists. Once
its canonical completed enveloping dg algebra carries the RTT-adapted
finite-quotient/shared-seed package and its compact core is realized as
an exact braided monoidal completion of a chosen finite-dimensional
factorization DK pair, the compact-core DK-5 equivalence and the
completed comparison are formal.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:yangian-typea-realization-criterion} applies to
\(U^{\mathrm{comp}}(\mathfrak{g}_{\cA})\), so this dg algebra model realizes the
standard type-$A$ H-level Yangian target and closes the local DK-4
packet on the canonical formal-moduli target by
Proposition~\ref{prop:yangian-canonical-envelope}. The additional
hypotheses are exactly the compact-core realization input of
Corollary~\ref{cor:yangian-typea-realization-plus-core-realization-orig},
with \(\mathcal{C}_Y^\omega\) realized inside
\(\operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})\) as
\(\mathcal{C}_{\mathfrak g}^\omega\). Therefore DK-5 closes.
\end{proof}

\begin{corollary}[Standard type-\texorpdfstring{$A$}{A} DK-4/DK-5 closure from spectral
vector-line realization; \ClaimStatusProvedHere]
\label{cor:yangian-typea-realization-plus-dg-packet-orig}
Assume the hypotheses of
Proposition~\ref{prop:yangian-typea-realization-criterion}. Assume
further that the spectral compact core admits an exact braided monoidal
functor \(J_q^\omega\) whose restriction to the vector evaluation line
is an equivalence onto the completed vector spectral line, as in
Proposition~\ref{prop:yangian-dk5-spectral-vector-line}.
Then the standard type-$A$ Yangian DK-4/DK-5 packet closes.

Equivalently, once the shared-bar-seed finite-quotient realization
package is in place, the dg half of DK-5 is already closed by the
canonical dg compact-core realization and its ind-completion, and the
ambient spectral category is formal from ind-completion of the spectral
compact core.

The only remaining categorical input is therefore the
spectral vector-line realization package; on the multiplicative
spectral realization locus this is equivalently the realization of the
standard spectral vector seed-and-shift datum, and
Corollary~\ref{cor:yangian-dk5-spectral-factorization-vector-line}
shows that vector-line realization already suffices, and
Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line}
shows that the compact core itself is then forced as the thick
braided-monoidal closure of that line inside the ambient ordered
factorization category, and
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-vector-line}
packages the resulting spectral DK-5 closure directly from that ambient
vector-line realization.

While
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}
and
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-one-seed}
and
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-schur-seed}
sharpen this further to one Schur-simple ambient vector seed together
with the one-parameter trigonometric seed-pair identity on its
dilation orbit, and
Corollary~\ref{thm:yangian-dk5-spectral-factorization-seed-single-line}
shows that under diagonal \(\mathfrak{sl}_M\)-equivariance and
highest-weight normalization this local packet contracts to one ordered
mixed-tensor line, while on the
equivariant multiplicative spectral realization locus of
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed},
the seed and shift data are intrinsic.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:yangian-typea-realization-criterion} supplies the
H-level dg-shifted realization and closes the local standard type-$A$
DK-4 packet. Proposition~\ref{prop:yangian-dk5-dg-extension-existence}
constructs the exact braided monoidal dg packet extension
\(J_Y^\omega\), Proposition~\ref{prop:yangian-dk5-dg-realization-formal}
makes it an equivalence onto the dg compact core, and
Corollary~\ref{cor:yangian-dk5-dg-packet-ind} constructs the ambient dg
module category as the ind-completion of that core. Thus the dg side
already satisfies the dg half of the input of
Corollary~\ref{cor:yangian-dk5-core-realization}. By
Proposition~\ref{prop:quantum-fd-vector-seed-shifts},
Propositions~\ref{prop:yangian-dk5-spectral-seed-shift-construction}
and~\ref{prop:yangian-dk5-spectral-core-shifts}, together with
Corollary~\ref{cor:yangian-dk5-spectral-seed-realization}, the same is
true on the spectral side with compact core \(\mathcal{C}_q^\omega\);
on the multiplicative spectral realization locus,
Corollary~\ref{cor:yangian-dk5-spectral-factorization-vector-line}
shows that vector-line realization already supplies the whole spectral
packet, and
Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line}
constructs the compact core itself as the thick braided-monoidal
closure of that line in the ambient ordered factorization category;
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-vector-line}
then packages the whole spectral DK-5 side directly from that ambient
vector-line realization;
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}
and
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-one-seed}
and
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-schur-seed}
show that, more sharply, one Schur-simple ambient vector seed already
supplies the whole object-level ambient route, while
Corollary~\ref{thm:yangian-dk5-spectral-factorization-seed-trig}
identifies the remaining explicit local comparison there with the
one-parameter trigonometric seed-pair identity on its dilation orbit,
and Corollary~\ref{thm:yangian-dk5-spectral-factorization-seed-single-line}
shows that under diagonal \(\mathfrak{sl}_M\)-equivariance and
highest-weight normalization this contracts further to one ordered
mixed-tensor line, and
Proposition~\ref{thm:yangian-dk5-spectral-factorization-seed-exchange}
sharpens that line to one scalar exchange coefficient family;
Corollary~\ref{thm:yangian-dk5-spectral-factorization-seed-exchange-mult}
shows that this scalar family already descends to the multiplicative
spectral ratio; equivalently,
Proposition~\ref{thm:yangian-dk5-spectral-factorization-seed-alt-mult}
rewrites it as one antisymmetric-channel character there;
and on the sharper equivariant multiplicative spectral
realization locus,
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed}
removes the seed and shift data as independent choices.
Hence the hypotheses of
Corollary~\ref{cor:yangian-dk5-core-realization} are satisfied, so
DK-5 closes.
\end{proof}
\fi
%% --- end of first \iffalse block (closures i--v) ---

\begin{corollary}[Canonical formal-moduli Yangian target: exact
remaining input after RTT-adapted realization;
\ClaimStatusProvedHere]
\label{cor:yangian-canonical-realization-to-spectral-seed}
Let
\[
\cA=\mathcal{Y}(\mathfrak{sl}_M),
\qquad
\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA}
\]
be the canonical H-level dg target of
Proposition~\ref{prop:yangian-canonical-hlevel-target}, and let
\[
U^{\mathrm{comp}}(\mathfrak{g}_{\cA})
\]
be its canonical associative dg model of
Proposition~\ref{prop:yangian-canonical-envelope}. Assume that the
hypotheses of Proposition~\ref{prop:yangian-typea-realization-criterion}
hold for \(U^{\mathrm{comp}}(\mathfrak{g}_{\cA})\). Then the canonical
formal-moduli target already carries the standard type-$A$ H-level dg
realization, the local DK-4 packet is closed, and the dg compact-core
side of DK-5 is formal.

Assume further that the spectral compact core \(\mathcal C_q^\omega\)
is realized as a full stable idempotent-complete braided-monoidal
subcategory of
\[
\Factord(\bC^\times;\QGspec(R_{\cA}))
\]
closed under the multiplicative dilations
\(\rho_a(z)=e^a z\), and that the exact braided-monoidal functor
\[
J_q^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\longrightarrow
\mathcal C_q^\omega
\]
intertwines the source loop-rotation family
\(\mathsf T_a^{\mathrm{fd}}\) with the target pullback family
\(\rho_a^*\). Define
\[
V^\omega(0):=J_q^\omega(V(0)).
\]
Then the hypotheses of
Corollary~\ref{cor:yangian-dk5-spectral-one-seed} are automatic.
Equivalently, on the canonical Yangian target, equivariant
multiplicative spectral realization removes the shift datum and the
base vector seed as independent inputs: the shift family is intrinsic
and the seed is canonical.

Equivalently, on the canonical Yangian target the only remaining
standard type-$A$ input is the spectral vector-line realization
package in the spectral compact core; on the equivariant
multiplicative spectral realization locus, this is equivalently the
realization of the standard spectral vector seed-and-shift datum and
contracts further to the realization functor together with one ambient
compatible
Schur-simple vector seed whose dilation orbit gives the spectral
vector line together with the one-parameter trigonometric seed-pair
identity on that orbit, and under diagonal
\(\mathfrak{sl}_M\)-equivariance and highest-weight normalization even
that local packet contracts first to one ordered mixed-tensor line and
then to one scalar exchange coefficient family.

Once
that ambient seed is placed
Corollary~\ref{cor:yangian-dk5-spectral-factorization-vector-line}
and Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line}
and Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-vector-line}
and Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}
and Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-one-seed}
and Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-schur-seed}
and Corollary~\ref{thm:yangian-dk5-spectral-factorization-seed-trig}
and Corollary~\ref{thm:yangian-dk5-spectral-factorization-seed-single-line}
and Proposition~\ref{thm:yangian-dk5-spectral-factorization-seed-exchange}
and Corollary~\ref{thm:yangian-dk5-spectral-factorization-seed-exchange-mult}
and Proposition~\ref{thm:yangian-dk5-spectral-factorization-seed-alt-mult}
make the rest formal.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:yangian-typea-realization-criterion} applied to
\(U^{\mathrm{comp}}(\mathfrak{g}_{\cA})\) gives the standard type-$A$
RTT-adapted dg realization, closes the local DK-4 packet, and reduces
the remaining input to the spectral vector-line realization package.
On the equivariant multiplicative spectral realization locus this is
equivalently the standard spectral vector seed-and-shift datum.
Proposition~\ref{prop:yangian-canonical-envelope} identifies
this dg model with the canonical formal-moduli target.

Under the additional multiplicative-spectral hypothesis,
Proposition~\ref{prop:yangian-dk5-spectral-factorization-shifts}
constructs the target shift family intrinsically as pullback along the
dilations \(\rho_a\), while the displayed definition makes the base
vector seed canonical. The assumed equivariance of \(J_q^\omega\)
with respect to source loop rotation and target pullback is exactly the
remaining compatibility hypothesis of
Corollary~\ref{cor:yangian-dk5-spectral-one-seed}. Therefore that
corollary applies and removes any separate seed-and-shift choice on the
canonical target. The final sentence is exactly this reformulation on
the canonical target.
\end{proof}

\begin{corollary}[Canonical formal-moduli Yangian target: the local
spectral packet contracts to one mixed-tensor line on the equivariant
multiplicative locus; \ClaimStatusProvedHere]
\label{cor:yangian-canonical-realization-to-single-line}
Assume the hypotheses of
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed}.
For \(c\in\mathbb C\), define
\[
V^\omega(c):=\rho_c^*V^\omega(0),
\]
and let
\[
\mathsf B_{0,c}^{\omega}\colon
V^\omega(0)\boxtimes V^\omega(c)
\xrightarrow{\sim}
V^\omega(c)\boxtimes V^\omega(0)
\]
be the associated ambient seed-pair braid operator on the realized
spectral compact core. Assume further that for every \(c\in\mathbb C\):
\begin{enumerate}[label=\textup{(\roman*)}]
\item \(\mathsf B_{0,c}^{\omega}\) intertwines the diagonal
 \(\mathfrak{sl}_M\)-action;
\item \(\mathsf B_{0,c}^{\omega}\) agrees with the standard source
 operator on the highest-weight line:
 \[
 \mathsf B_{0,c}^{\omega}(e_1\otimes e_1)
 =
 \mathsf B_{0,c}^{\mathrm{fd}}(e_1\otimes e_1).
 \]
\end{enumerate}
Then the remaining explicit local spectral comparison on the canonical
target is exactly the one-parameter mixed-tensor identity
\[
\mathsf B_{0,c}^{\omega}(e_1\otimes e_2)
=
\mathsf B_{0,c}^{\mathrm{fd}}(e_1\otimes e_2)
\qquad (c\in\mathbb C).
\]

Equivalently, on the equivariant multiplicative spectral realization
locus of the canonical target, once the seed and shift data are
canonical and the diagonal symmetry/highest-weight normalization are in
place, the local spectral packet is no longer a whole trigonometric
family: it contracts to one ordered mixed-tensor line family.
\end{corollary}

\begin{proof}
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed}
constructs the canonical seed \(V^\omega(0)\) and the intrinsic shift
family \(\rho_c^*\) on the equivariant multiplicative spectral
realization locus. Therefore the ambient seed-pair operators
\(\mathsf B_{0,c}^{\omega}\) are exactly the operators to which
Corollary~\ref{thm:yangian-dk5-spectral-factorization-seed-single-line}
applies, with \(V^{\mathrm{mult}}(0)=V^\omega(0)\). The two extra
hypotheses here are precisely the diagonal
\(\mathfrak{sl}_M\)-equivariance and highest-weight normalization
hypotheses required there. Hence that corollary identifies the
remaining local spectral comparison with the displayed mixed-tensor
family.
\end{proof}

\begin{corollary}[Canonical formal-moduli Yangian target: the local
spectral packet contracts to one exchange coefficient family on the
equivariant multiplicative locus; \ClaimStatusProvedHere]
\label{cor:yangian-canonical-realization-to-exchange}
Assume the hypotheses of
Corollary~\ref{cor:yangian-canonical-realization-to-single-line}, and
assume \(M\ge 2\). For every \(c\in\mathbb C\), write uniquely
\[
\mathsf B_{0,c}^{\omega}(e_1\otimes e_2)
=
\alpha^\omega(c)\,e_1\otimes e_2
+\beta^\omega(c)\,e_2\otimes e_1
\]
and
\[
\mathsf B_{0,c}^{\mathrm{fd}}(e_1\otimes e_2)
=
\alpha^{\mathrm{fd}}(c)\,e_1\otimes e_2
+\beta^{\mathrm{fd}}(c)\,e_2\otimes e_1.
\]
Then the remaining explicit local spectral comparison on the canonical
target is exactly the scalar identity
\[
\beta^\omega(c)=\beta^{\mathrm{fd}}(c)
\qquad (c\in\mathbb C).
\]

Equivalently, on the equivariant multiplicative spectral realization
locus of the canonical target, once the seed and shift data are
canonical and the diagonal symmetry/highest-weight normalization are in
place, the local spectral packet contracts from one ordered
mixed-tensor line family to one scalar exchange coefficient family.
\end{corollary}

\begin{proof}
Corollary~\ref{cor:yangian-canonical-realization-to-single-line}
identifies the remaining local spectral comparison on the canonical
target with the mixed-tensor family
\[
\mathsf B_{0,c}^{\omega}(e_1\otimes e_2)
=
\mathsf B_{0,c}^{\mathrm{fd}}(e_1\otimes e_2)
\qquad (c\in\mathbb C).
\]
Now apply
Proposition~\ref{thm:yangian-dk5-spectral-factorization-seed-exchange}
with \(V^{\mathrm{mult}}(0)=V^\omega(0)\) and
\(\mathsf B_{0,c}^{\mathrm{mult}}=\mathsf B_{0,c}^{\omega}\).
\end{proof}

\begin{corollary}[Canonical formal-moduli Yangian target: the local
spectral packet descends to one multiplicative-ratio scalar family;
\ClaimStatusProvedHere]
\label{cor:yangian-canonical-realization-to-exchange-mult}
Assume the hypotheses of
Corollary~\ref{cor:yangian-canonical-realization-to-exchange}. Then
\[
\beta^\omega(c+2\pi i)=\beta^\omega(c)
\qquad (c\in\mathbb C),
\]
so the canonical-target exchange coefficient descends uniquely to a
scalar function
\[
\beta_\times^\omega
\]
of the multiplicative spectral ratio with
\[
\beta^\omega(c)=\beta_\times^\omega(e^c).
\]
The remaining explicit local spectral comparison on the canonical
target is therefore exactly
\[
\beta_\times^\omega=\beta_\times^{\mathrm{fd}}.
\]

Equivalently, on the equivariant multiplicative spectral realization
locus of the canonical target, the local spectral packet is one scalar
function on the multiplicative spectral line, not a family on its
additive logarithmic cover.
\end{corollary}

\begin{proof}
By
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed},
the canonical target shift family is the ambient dilation pullback
family \(\rho_c^*\), so
\[
V^\omega(c)=\rho_c^*V^\omega(0).
\]
Since \(\rho_{c+2\pi i}=\rho_c\), one has
\[
V^\omega(c+2\pi i)=V^\omega(c)
\]
and therefore
\[
\mathsf B_{0,c+2\pi i}^{\omega}
=
\mathsf B_{0,c}^{\omega}.
\]
Taking the coefficient of \(e_2\otimes e_1\) in the expansion of
\(\mathsf B_{0,c}^{\omega}(e_1\otimes e_2)\) gives the displayed
periodicity of \(\beta^\omega(c)\). The source side already descends
by
Corollary~\ref{thm:yangian-dk5-spectral-factorization-seed-exchange-mult},
so the final identity is just
Corollary~\ref{cor:yangian-canonical-realization-to-exchange}
rewritten on the multiplicative ratio line.
\end{proof}

\begin{corollary}[Canonical formal-moduli Yangian target: the local
spectral packet is the antisymmetric-channel character on the
multiplicative spectral line; \ClaimStatusProvedHere]
\label{cor:yangian-canonical-realization-to-alt-mult}
Assume the hypotheses of
Corollary~\ref{cor:yangian-canonical-realization-to-exchange-mult}, and
assume \(M\ge 2\). Then there exists a unique scalar function
\[
\lambda_{\mathrm{alt},\times}^{\omega}
\]
of the multiplicative spectral ratio such that
\[
\mathsf B_{0,c}^{\omega}
(e_1\otimes e_2-e_2\otimes e_1)
=
\lambda_{\mathrm{alt},\times}^{\omega}(e^c)
(e_1\otimes e_2-e_2\otimes e_1).
\]
The remaining explicit local spectral comparison on the canonical
target is exactly
\[
\lambda_{\mathrm{alt},\times}^{\omega}
=
\lambda_{\mathrm{alt},\times}^{\mathrm{fd}}.
\]

Equivalently, on the equivariant multiplicative spectral realization
locus of the canonical target, the local spectral packet is one scalar
character on the highest-weight antisymmetric channel over the
multiplicative spectral line.
\end{corollary}

\begin{proof}
Apply
Proposition~\ref{thm:yangian-dk5-spectral-factorization-seed-alt-mult}
with \(V^{\mathrm{mult}}(0)=V^\omega(0)\) and
\(\mathsf B_{0,c}^{\mathrm{mult}}=\mathsf B_{0,c}^{\omega}\). The
hypotheses needed there are exactly those supplied by
Corollary~\ref{cor:yangian-canonical-realization-to-exchange-mult}.
\end{proof}

%% --- second \iffalse block (closures vi--vii) ---
\iffalse
\begin{corollary}[Canonical formal-moduli Yangian target closes
DK-4/DK-5 from one canonical spectral seed on the equivariant
multiplicative locus; \ClaimStatusProvedHere]
\label{cor:yangian-canonical-realization-plus-one-seed-orig}
Assume the hypotheses of
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed}.
Then the standard type-$A$ Yangian DK-4/DK-5 packet closes on the
canonical formal-moduli target.

Equivalently, once the canonical completed enveloping dg algebra
\(U^{\mathrm{comp}}(\mathfrak{g}_{\cA})\) carries the RTT-adapted
finite-quotient/shared-seed package and the spectral compact core is
realized equivariantly for multiplicative dilations, it is enough to
place the single canonical spectral seed
\[
V^\omega(0):=J_q^\omega(V(0)).
\]
The shift family is then intrinsic, the full spectral vector packet is
forced, and DK-4/DK-5 closes on the canonical target.
\end{corollary}

\begin{proof}
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed}
makes the hypotheses of
Corollary~\ref{cor:yangian-dk5-spectral-one-seed} automatic on the
canonical target. Therefore the completed vector line, ordered vector
packet, completed fundamental packet, ordered tensor-generator packet,
spectral compact core, and ambient spectral category are all formal.
In particular, the vector-line hypothesis of
Corollary~\ref{cor:yangian-canonical-realization-plus-vector-line-orig} is
satisfied. Applying that corollary closes DK-4/DK-5.
\end{proof}

\begin{corollary}[Canonical formal-moduli Yangian target closes
DK-4/DK-5 from spectral vector-line realization;
\ClaimStatusProvedHere]
\label{cor:yangian-canonical-realization-plus-vector-line-orig}
Let
\[
\cA=\mathcal{Y}(\mathfrak{sl}_M),
\qquad
\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA}
\]
be the canonical H-level dg target of
Proposition~\ref{prop:yangian-canonical-hlevel-target}, and let
\[
U^{\mathrm{comp}}(\mathfrak{g}_{\cA})
\]
be its canonical associative dg model of
Proposition~\ref{prop:yangian-canonical-envelope}. Assume that the
hypotheses of Proposition~\ref{prop:yangian-typea-realization-criterion}
hold for \(U^{\mathrm{comp}}(\mathfrak{g}_{\cA})\). Assume further
that the spectral compact core admits an exact braided monoidal functor
\[
J_q^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\longrightarrow
\mathcal C_q^\omega
\]
whose restriction to the vector evaluation line is an equivalence onto
the completed vector spectral line, as in
Proposition~\ref{prop:yangian-dk5-spectral-vector-line}. Then the
standard type-$A$ Yangian DK-4/DK-5 packet closes on the canonical
formal-moduli target.

Equivalently, once the canonical completed enveloping dg algebra
carries the RTT-adapted finite-quotient/shared-seed package, it is
enough to realize the standard vector evaluation line on the spectral
side. The dg compact core and ambient dg category are already formal,
and the spectral compact core, ambient spectral category, compact-core
comparison, and completed comparison then become formal as well. On
the multiplicative spectral factorization locus,
Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line}
shows that the spectral compact core is forced as the thick
braided-monoidal closure of that realized vector line.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:yangian-typea-realization-criterion} applies to
\(U^{\mathrm{comp}}(\mathfrak{g}_{\cA})\), so the canonical
formal-moduli target already carries the standard type-$A$ dg-shifted
realization and the local DK-4 packet is closed. The additional
vector-line hypothesis is exactly the remaining spectral input of
Corollary~\ref{cor:yangian-typea-realization-plus-dg-packet-orig}, so that
corollary applies and closes DK-4/DK-5 on the canonical target. The
final sentence is the multiplicative factorization refinement supplied
by Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line}.
\end{proof}
\fi
%% --- end of second \iffalse block (closures vi--vii) ---

\begin{remark}[Rational vs.\ trigonometric DK]
\label{rem:rational-trigonometric-dk}
\index{Drinfeld--Kohno!rational vs trigonometric}
The DK square takes different forms depending on the $R$-matrix type:

\emph{Rational DK}
\textup{(}Theorem~\textup{\ref{thm:derived-dk-yangian})}.
The Yangian $R$-matrix $R(u) = 1 - \hbar P/u$ is rational
in the additive spectral parameter $u$. Koszul duality sends
$\hbar \to -\hbar$, i.e., $R(u) \to R^{-1}(u)$. The bar
complex uses the propagator $d\log(z_i - z_j)$ on the
FM compactification of $\bC$.

\emph{Trigonometric DK}
\textup{(}Remark~\textup{\ref{rem:yangian-quantum-group})}.
The quantum loop algebra $U_q(\widehat{\mathfrak{g}})$ has
trigonometric $R$-matrix $R(u/v)$ in the multiplicative
parameter. Koszul duality sends $q \to q^{-1}$. The bar
complex uses the propagator $d\log(z_i/z_j)$ on the
FM compactification of $\bC^\times$.

The Kazhdan functor $\Phi_K$ intertwines the rational and
trigonometric pictures via the exponential map $u \mapsto e^u$,
$\bC \to \bC^\times$. The DK
square~\eqref{eq:dk-square-yangian} encodes the commutativity
of this intertwining with bar-cobar duality.
\end{remark}

The Yangian chapter reveals the $\Eone$-chiral face of the theory.
The chain-level / evaluation-locus derived Drinfeld--Kohno theorem
(Theorems~\ref{thm:derived-dk-affine}
and~\ref{thm:derived-dk-yangian}) proves that bar-cobar duality
\emph{geometrically implements} the quantum group involution
$q \mapsto q^{-1}$, via orientation reversal on ordered
configuration spaces. The $\Einf$-chiral examples of the preceding
chapters all have commutative factorization structure; the Yangian is
the first object whose Koszul duality intertwines genuinely
noncommutative (braided) monoidal data. The theorematic endpoint is
the conditional DK-2/3 extension criterion for finite-dimensional
type~$A$ (Theorem~\ref{conj:dk-fd-typeA}), which reduces the extension
of the evaluation-locus factorization comparison
\textup{(}Theorem~\ref{thm:factorization-dk-eval}\textup{)} to thick
generation plus the ambient extension/comparison package.
The MC4 structural framework underlying DK-4 is proved (Theorem~\ref{thm:completed-bar-cobar-strong}; the algebraic identification remains open, Conjecture~\ref{conj:dk4-formal-moduli}), and with only the all-types CG/core
level of MC3 proved while the remaining completion packet stays
open, DK-5 is reduced to that post-core extension problem for
Yangian towers. The remaining open problem is the extension to
the full category~$\mathcal{O}$ (beyond the evaluation-generated core).
The full DK-5 triple-bridge comparison is the natural
$\Eone$-chiral bridge to the modular Koszul package
\ifannalsedition\else
(\S\ref{sec:modular-koszul-programme})
\fi.

%% ================================================================
%% § The modular dg-shifted Yangian
%% ================================================================
\subsection{The modular dg-shifted Yangian}
\label{sec:modular-dg-shifted-yangian}
\index{Yangian!modular dg-shifted|textbf}

The dg-shifted Yangian of
Dimofte--Niu--Py~\cite{DNP25}
is a genus-zero, local object: it packages line-operator OPE on
$\bC$ into a dg algebra with translation operator and
Maurer--Cartan kernel~$r(z)$. The modular extension promoted
here is intended to organize both the line-operator OPE and the
stable-curve gluing data in a single algebraic envelope.

The proposed modular $R$-matrix $R_T^{\mathrm{mod}}(z;\hbar)$, if the
Maurer--Cartan element of
Conjecture~\ref{conj:modular-yang-baxter} exists, is intended to be
the ordered $\Eone$-factorization specialization of the universal MC
element~$\Theta_\cA$ (Theorem~\ref{thm:mc2-bar-intrinsic}). On that
conjectural surface, the shadow obstruction projections would admit the
 following representation-theoretic reading: the scalar level
 $\kappa$ governs the genus-$1$ scalar trace unconditionally and, on
 the proved uniform-weight scalar lane, the full genus tower via the
 $\hat{A}$-genus; the cubic
 shadow~$C$ controls the genus-zero $r$-matrix package, and quartic or
higher shadows govern the quantum corrections such as
$\hbar^2 r_{T,1}(z)$. The benchmark and conditional computations in
this section are organized as projections in the pronilpotent
completion of the convolution algebra $\gAmod$
(Definition~\ref{def:modular-convolution-dg-lie}).

\providecommand{\ModEnv}{\operatorname{ModEnv}}
\providecommand{\Ymod}{Y^{\mathrm{mod}}}

\begin{definition}[Modular dg-shifted Yangian as pro-MC object;
\ClaimStatusConjectured]
\label{def:modular-yangian-pro}
\label{def:modular-yangian}
\index{Yangian!modular dg-shifted!definition}
\index{Yangian!modular dg-shifted!pro-MC object}
Let $T$ be a holomorphic-topological theory with boundary
condition~$B$ and Koszul dual~$\cA_T^!$. The
\emph{modular convolution algebra} is the dg~Lie algebra
(the strict model $\Convstr$ of $\Convinf$; Convention~\ref{rem:two-level-convention})
\[
 \mathcal{L}_T^{\mathrm{mod}}
 \;:=\;
 \prod_{2g-2+n>0}
 \Hom\bigl(
 C_\bullet(\overline{\mathcal{M}}_{g,n+1})
 \otimes (\cA_T^!)^{\widehat{\otimes}\,n},\;
 \cA_T^!
 \bigr)[1]
\]
equipped with the following structure.

\medskip\noindent\textbf{Differential.}\;
The differential $d = d_{\mathrm{int}} + d_{\mathrm{mod}}$
has two summands:
\begin{itemize}
\item $d_{\mathrm{int}}(\phi)$ is the internal $A_\infty$
 differential on~$\cA_T^!$, acting on inputs and output of~$\phi$;
\item $d_{\mathrm{mod}}(\phi)$ is the boundary operator
 dual to the stable-curve boundary
 $\partial \colon \overline{\mathcal{M}}_{g,n+1}
 \to \coprod_{g_1+g_2=g,\,S_1 \sqcup S_2}
 \overline{\mathcal{M}}_{g_1,|S_1|+1}
 \times \overline{\mathcal{M}}_{g_2,|S_2|+1}$
 (and the non-separating boundary), acting by precomposition
 on the chain argument of~$\phi$.
\end{itemize}

\noindent\textbf{Lie bracket.}\;
For $\phi \in \mathcal{L}_T^{\mathrm{mod}}$ of type~$(g_1,n)$
and $\psi$ of type~$(g_2,m)$, the bracket
$[\phi,\psi]$ lives in type~$(g_1+g_2,\,n+m-1)$ and is
\[
 [\phi,\psi](\gamma;\, a_1,\ldots,a_{n+m-1})
 \;=\;
 \sum_{\substack{I \sqcup J = \{1,\ldots,n+m-1\}\\
 |I|=n-1,\; |J|=m}}
 \pm\;\phi\bigl(\gamma_I;\, a_I,\,
 \psi(\gamma_J;\, a_J)\bigr),
\]
where $\gamma_I,\gamma_J$ are the chain factors induced by
stable-graph composition and the sign is the Koszul sign
from the graded-symmetric interchange. The internal edge
connecting one output of~$\psi$ to one input of~$\phi$
carries the propagator~$r_T(z)$.

\noindent\textbf{Filtration and pronilpotent completion.}\;
Define
\[
 F^N \mathcal{L}_T^{\mathrm{mod}}
 \;:=\;
 \prod_{2g-2+n \ge N}
 \Hom\bigl(
 C_\bullet(\overline{\mathcal{M}}_{g,n+1})
 \otimes (\cA_T^!)^{\widehat{\otimes}\,n},\;
 \cA_T^!
 \bigr)[1].
\]
Since the bracket maps
$F^{N_1} \times F^{N_2} \to F^{N_1+N_2}$,
this is a Lie filtration and the separated completion
\[
 \Ymod_T
 \;:=\;
 \widehat{\mathcal{L}}_T^{\mathrm{mod}}
 \;:=\;
 \varprojlim_N\;
 \mathcal{L}_T^{\mathrm{mod}} \big/ F^{N+1}
\]
is a pronilpotent dg Lie algebra. Since the original
$\mathcal{L}_T^{\mathrm{mod}}$ is already a product over
$(g,n)$-components (each finite-dimensional in the
genus-graded sense), the completion map is an isomorphism:
$\widehat{\mathcal{L}}_T^{\mathrm{mod}} \cong
\mathcal{L}_T^{\mathrm{mod}}$.
On the conjectural surface where the modular line-operator package
admits the intended compatible algebra structure, that structure is
encoded by a Maurer--Cartan element
\[
 R_T^{\mathrm{mod}}(z;\hbar)
 \;=\;
 \sum_{g \ge 0} \hbar^{2g}\, r_{T,g}(z)
 \;\in\;
 \operatorname{MC}(\Ymod_T),
\]
and the stable-graph Yang--Baxter equation is then the
corresponding Maurer--Cartan equation in~$\Ymod_T$.

The usual dg-shifted Yangian
$\Ydg_{\cA}$
(Definition~\ref{def:dg-shifted-yangian})
is recovered only at the genus-zero sector of this package: the
coefficient $r_{T,0}(z)=r_T(z)$ and the associated genus-zero
operations reproduce the dg-shifted Yangian data.
The definition constructs the ambient pro-dg~Lie algebra;
\emph{populating} it with an MC~element
$R_T^{\mathrm{mod}} \in \MC(\Ymod_T)$ is the content of
Conjecture~\ref{conj:modular-yang-baxter}.
\end{definition}

\begin{remark}[Modular $R$-matrix as conjectural MC restriction]
\label{rem:modular-yangian-chriss-ginzburg}
On that conjectural surface, the genus-zero sector of the pro-MC
package reduces to the dg-shifted Yangian of
Dimofte--Niu--Py~\cite{DNP25}. The modular
completion is a single algebraic structure (a pronilpotent
dg~Lie algebra), not a collection of data. On the conjectural
surface where Conjecture~\ref{conj:modular-yang-baxter} is solved,
the resulting algebra structure is encoded by a Maurer--Cartan
element.

More precisely, the intended kernel
$R_T^{\mathrm{mod}}(z;\hbar)$ is intended to be the ordered
$\Eone$-factorization restriction of the universal MC
element~$\Theta_\cA$ of Theorem~\ref{thm:mc2-bar-intrinsic}. On that
conjectural surface, the
shadow obstruction decomposition
(Corollary~\ref{cor:shadow-extraction}) reads as follows in the
Yangian setting:
\begin{itemize}
\item \textbf{Degree 2} (scalar level $\kappa$): the genus tower
 is governed unconditionally at genus~$1$ by the scalar trace
 $\kappa \cdot \lambda_1$; on the proved uniform-weight scalar lane
 this further specializes to the full $\hat{A}$-genus generating
 function \ifannalsedition\else
(Chapter~\ref{ch:genus-expansions})
\fi;
\item \textbf{Degree 3} (cubic shadow $C$): the classical
 $r$-matrix $r_{T,0}(z)$ and the classical Yang--Baxter equation
 $[r_{12}, r_{13}] + [r_{12}, r_{23}] + [r_{13}, r_{23}] = 0$;
\item \textbf{Degree $\geq 4$} (quartic and higher): the quantum
 corrections $r_{T,g}$ for $g \geq 1$ and the stable-graph
 Yang--Baxter equation~\eqref{eq:stable-graph-yb}.
\end{itemize}
The Yangian shadow obstruction tower is \emph{infinite} (the $\mathcal{W}_N$-type
archetype, not the Gaussian or contact archetype) because the quantum
corrections do not terminate at any finite degree.

At the full homotopy level, $\mathcal{L}_T^{\mathrm{mod}}$ carries
a \emph{quantum $L_\infty$-structure}
(Theorem~\ref{thm:modular-quantum-linfty}): operations
$\{\ell_n^{(g)}\}$ where $\ell_2^{(0)}$ is the dg~bracket above,
$\ell_n^{(0)}$ for $n \geq 3$ are the higher operadic brackets from
homotopy transfer through
$C_*(\overline{\mathcal{M}}_{0,n+1})$, and $\ell_n^{(g)}$ for
$g \geq 1$ are the higher-genus Feynman amplitudes. If the modular
kernel of Conjecture~\ref{conj:modular-yang-baxter} exists, then it is
an MC~element for the full quantum $L_\infty$-structure, and the
stable-graph Yang--Baxter
equation~\eqref{eq:stable-graph-yb} is the leading-order truncation
of this quantum MC~equation.
\end{remark}

\begin{conjecture}[Modular Yang--Baxter package;
\ClaimStatusConjectured]
\label{conj:modular-yang-baxter}
\index{Yang--Baxter!modular stable-graph refinement}
For every holomorphic-topological theory~$T$ with Koszul-dual
boundary condition~$B$, there exists a Maurer--Cartan element
$R_T^{\mathrm{mod}}(z;\hbar) \in \operatorname{MC}(\Ymod_T)$
(Definition~\ref{def:modular-yangian-pro}) whose genus-refined
components $r_{T,g}(z)$ satisfy the \emph{stable-graph
Yang--Baxter equation}: for each $g \ge 0$,
\begin{equation}\label{eq:stable-graph-yb}
 d_{\mathrm{mod}}\, r_{T,g}(z)
 \;+\;
 \sum_{g_1+g_2=g}
 \bigl[r_{T,g_1}(z),\, r_{T,g_2}(z)\bigr]_{\mathrm{graph}}
 \;+\;
 \Delta\bigl(r_{T,g-1}(z)\bigr)
 \;=\; 0,
\end{equation}
where $[\cdot,\cdot]_{\mathrm{graph}}$ is the Lie bracket in
$\mathcal{L}_T^{\mathrm{mod}}$ (graph composition with the
propagator on the internal edge), $\Delta$ is the genus-loop
operator from non-separating degeneration of
$\overline{\mathcal{M}}_{g,n}$ (contracting a single handle),
and $r_{T,-1} := 0$ by convention. The initial condition is
$r_{T,0}(z) = r_T(z)$, the genus-zero kernel.

At genus zero the
terms with $\Delta$ and $g_1,g_2 > 0$ vanish, and
\eqref{eq:stable-graph-yb} reduces to
$d_{\mathrm{mod}}\,r_{T,0} + [r_{T,0},r_{T,0}]_{\mathrm{graph}} = 0$,
which is the $A_\infty$ Yang--Baxter equation
of~\cite{DNP25}.
\end{conjecture}

\begin{remark}[Relation to the DK ladder]
\label{rem:modular-yangian-dk}
\index{Drinfeld--Kohno!DK-5!modular Yangian}
The modular dg-shifted Yangian $\Ymod_T$ should be the natural
target of a DK-5 level comparison
(Conjecture~\ref{conj:dk5-infty-pbw}): the bridge from the
$\Eone$-chiral factorization category to the modular Koszul
package. Its existence first requires extending beyond the evaluation-generated
core to the full Ran space, since the
stable-graph completion requires control of the factorization
category on the full module category, not merely on the evaluation
locus for finite-dimensional modules. MC3 is proved for all simple
types on the evaluation-generated core
\textup{(}Corollary~\ref{cor:mc3-all-types}\textup{)}; the residual
problem is the DK-4/5 extension/completion packet
\textup{(}Conjecture~\ref{conj:dk-compacts-completion}\textup{)},
which extends beyond evaluation modules into the full category.
Once that packet is supplied, Conjecture~\ref{conj:dk5-infty-pbw}
isolates the remaining DK-5 bridge step as the
exponential/PBW comparison. The genus-refined Maurer--Cartan
equation of Conjecture~\ref{conj:modular-yang-baxter} is a
single organizing principle for both the genus-zero DK square
(Remark~\ref{rem:dk-square-geometry}) and the higher-genus
complementarity data of Theorem~C.
\end{remark}

% ==========================================
% MODULAR YANG-BAXTER PACKAGE AND HOLOGRAPHIC LINE OPERATORS
% ==========================================

\subsection{The modular Yang--Baxter package and holographic line operators}
\label{subsec:modular-yb-holographic}
\index{Yang--Baxter!modular package}
\index{line operators!holographic completion}

The modular dg-shifted Yangian $\Ymod_T$ of
Definition~\ref{def:modular-yangian-pro} is the ambient
pronilpotent dg Lie algebra intended to organize
stable-curve gluing \emph{and} spectral line-operator data in a
single algebraic package. The ambient ingredients together with the
conjectural kernel data are as follows; this
package is strictly richer than a modular envelope.

\subsubsection{The modular $r$-matrix expansion}

\begin{definition}[Modular total kernel]
\label{def:modular-total-kernel}
\index{r-matrix@$r$-matrix!modular total kernel}
A \emph{modular total kernel} is a formal $\hbar$-completed $r$-matrix
\begin{equation}\label{eq:modular-total-kernel}
 R_T^{\mathrm{mod}}(z;\hbar)
 \;:=\;
 \sum_{g \ge 0} \hbar^{2g}\, r_{T,g}(z),
 \qquad
 r_{T,0}(z) = r_T(z),
\end{equation}
where each genus-$g$ coefficient lives in
\begin{equation}\label{eq:r-coeff-space}
 r_{T,g}(z)
 \;\in\;
 H^\bullet\bigl(\overline{\mathcal{M}}_{g,2}\bigr)
 \otimes
 \cA_T^! \,\widehat{\otimes}\,
 \cA_T^!\bigl(\!(z^{-1})\!\bigr).
\end{equation}
By Conjecture~\ref{conj:modular-yang-baxter}, such a total kernel
$R_T^{\mathrm{mod}}(z;\hbar)$ is a Maurer--Cartan element in a
pronilpotent dg Lie algebra built from the boundary stratification
of $\overline{\mathcal{M}}_{g,n}$. The Maurer--Cartan condition
encodes both the genus-zero $A_\infty$ Yang--Baxter equation and
its all-genera stable-graph refinement.
\end{definition}

\subsubsection{An algebraic line-operator model}

\begin{definition}[Algebraic line-operator model]
\label{def:line-operator-category-yb}
\index{line operators!category $\mathcal{C}_T$}
For the purposes of this subsection, define the
\emph{algebraic line-operator model} associated to the theory~$T$ by
\begin{equation}\label{eq:line-cat}
 \mathcal{C}_T
 \;:=\;
 \cA_T^!\text{-}\mathrm{mod},
\end{equation}
the dg category of modules for the Koszul dual algebra. When a
compatible spectral kernel $r_T(z)$ is supplied, this algebraic model
acquires the corresponding $z$-dependent comultiplication:
\begin{equation}\label{eq:twisted-coproduct}
 \Delta_z \colon
 \cA_T^!
 \;\longrightarrow\;
 \cA_T^! \,\widehat{\otimes}_{r_T(z)}\,
 \cA_T^!\bigl(\!(z^{-1})\!\bigr).
\end{equation}
\end{definition}

\begin{conjecture}[Consistency via $D^2 = 0$; \ClaimStatusConjectured]
\label{conj:ainfty-yb-consistency}%
\index{Yang--Baxter!A-infinity consistency@$A_\infty$ consistency}
The $A_\infty$ Yang--Baxter equation for the spectral kernel $r(z)$
is equivalent to the condition $D^2 = 0$ on the $d_r$-twisted
modular bar complex of $\cA_T$. This is the algebraic
condition that upgrades ``modular gluing'' (stable-curve composition
in the Feynman transform) to the corresponding \emph{algebraic
spectral defect model} incorporating line-operator OPE data.
\end{conjecture}

\subsubsection{Beyond the modular envelope}

\begin{remark}[What the modular envelope does not see]
\label{rem:beyond-modular-envelope}
\index{modular envelope!limitations}
A modular envelope remembers the composition of operations along stable
curves (the Feynman transform of the modular operad
$\{\overline{\mathcal{M}}_{g,n}\}$) but it does \emph{not} encode:
\begin{enumerate}
\item the \emph{Maurer--Cartan moduli problem}, parametrizing
 consistent couplings of the theory to background fields and defects;
\item the \emph{bulk-boundary map}
 $\cA_{\mathrm{bulk}} \simeq Z_{\mathrm{der}}(\cA_\partial)$
 to the derived center;
\item the \emph{Poisson bracket and higher stress tensor}, the
 shifted-symplectic geometry of
 Theorem~\ref{thm:ambient-complementarity-fmp};
\item the \emph{algebraic line-operator model}
 $\mathcal{C}_T := \cA_T^!\text{-}\mathrm{mod}$ and, when equipped
 with a compatible spectral kernel, its spectral tensor
 structure;
\item the \emph{spectral $r(z)$-matrix} and the $A_\infty$ Yang--Baxter
 equation that governs it.
\end{enumerate}
The dg-shifted Yangian package $\Ymod_T$ provides the ambient
algebraic home for this additional structure. Its genus-zero
sector recovers the dg-shifted Yangian data of
Definition~\ref{def:dg-shifted-yangian}; once the conjectural
kernel data of Conjecture~\ref{conj:modular-yang-baxter} are
supplied, the full modular completion becomes the algebraic home for
all-genera defect OPE coefficients and holographic line-operator
amplitudes.
\end{remark}

%% ================================================================
%% § Restricted DK-5 and DS on primitive triples
%% ================================================================
\subsubsection{DK-5: modular Yangian-shadow equivalence}

\begin{conjecture}[DK-5: modular Yangian-shadow equivalence;
\ClaimStatusConjectured]
\label{conj:dk5-restricted}
\index{Drinfeld--Kohno!DK-5!modular Yangian-shadow equivalence}
\index{Yangian!modular dg-shifted!DK-5 equivalence}
Let~$\cA$ be a modular Koszul algebra with
multiplicity-free $\ell$-weight spectrum
\textup{(}in the sense of
Theorem~\textup{\ref{thm:categorical-cg-all-types}}\textup{)}.
The following data are equivalent:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The modular dg-shifted Yangian $R$-matrix
 $R_\cA^{\mathrm{mod}}(z;\hbar)
 \in \operatorname{MC}(\Ymod_\cA)$
 \textup{(}Definition~\textup{\ref{def:modular-yangian-pro}},
 Conjecture~\textup{\ref{conj:modular-yang-baxter}}\textup{)}.
\item The universal MC element
 $\Theta_\cA \in \operatorname{MC}(\fg_\cA^{\mathrm{mod}})$
 \textup{(}Theorem~\textup{\ref{thm:mc2-bar-intrinsic}}\textup{)}.
\item The shadow obstruction tower
 $\{\Theta_\cA^{\leq r}\}_{r \geq 2}$
 together with its clutching laws
 \textup{(}Theorem~\textup{\ref{thm:recursive-existence}}\textup{)}.
\end{enumerate}
The equivalence
\textup{(i)}\,$\Leftrightarrow$\,\textup{(ii)}
is mediated by collision-residue extraction:
at degree~$2$, $r_\cA(z) = \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$
\textup{(}Theorem~\textup{\ref{thm:r-matrix-koszul-dual-inverse}}\textup{)},
extended to all degrees by the planted-forest expansion.
At genus~$g$, the coefficient
$r_{\cA,g}(z) \in H^\bullet(\overline{\mathcal{M}}_{g,2})
\otimes \cA^! \,\widehat{\otimes}\, \cA^!(\!(z^{-1})\!)$
is the genus-$g$ binary projection of~$\Theta_\cA$.
The equivalence
\textup{(ii)}\,$\Leftrightarrow$\,\textup{(iii)}
is the inverse limit
$\Theta_\cA = \varprojlim \Theta_\cA^{\leq r}$.
\end{conjecture}

\begin{remark}[Proved and open components of DK-5]
\label{rem:dk5-restricted-status}
\index{Drinfeld--Kohno!DK-5!status of components}
The three data of Conjecture~\ref{conj:dk5-restricted} exist
individually:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $\Theta_\cA$ exists unconditionally
 \textup{(}Theorem~\ref{thm:mc2-bar-intrinsic}:
 $\Theta_\cA := D_\cA - d_0$ is MC because
 $D_\cA^2 = 0$\textup{)}.
\item The inverse limit
 $\Theta_\cA = \varprojlim \Theta_\cA^{\leq r}$ exists
 \textup{(}Theorem~\ref{thm:recursive-existence}\textup{)},
 so~\textup{(ii)}\,$\Leftrightarrow$\,\textup{(iii)} is proved.
\item The collision-residue extraction
 $r_\cA(z)
 = \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$
 at genus~$0$, degree~$2$ is proved
 \textup{(}Theorem~\ref{thm:r-matrix-koszul-dual-inverse}\textup{)}.
\end{enumerate}
What is \emph{open} is the full modular bridge: confirming that
the genus-$g$ coefficients $r_{\cA,g}(z)$ of the modular total
kernel
\textup{(}Definition~\ref{def:modular-total-kernel}\textup{)}
satisfy the stable-graph Yang--Baxter
equation~\eqref{eq:stable-graph-yb} and that this MC element,
together with the ambient pronilpotent dg~Lie
algebra~$\Ymod_\cA$, determines~$\Theta_\cA$
uniquely. That is, the conjectural content is
the reconstruction of the full MC element from the ordered
$\Eone$-factorization data: one must show that
the planted-forest expansion of all-degree, all-genera
collision residues
$\operatorname{Res}^{\mathrm{coll}}_{g,k}(\Theta_\cA)$
assembles into a Maurer--Cartan element of~$\Ymod_\cA$
that recovers~$\Theta_\cA$.

The multiplicity-free $\ell$-weight hypothesis enters through
Theorem~\ref{thm:categorical-cg-all-types}: it ensures
that the categorical Clebsch--Gordan closure holds at all
simple types, so the factorization category on the
evaluation-generated core is under control. Without this
hypothesis, the DK-5 equivalence is not expected to hold,
since the modular Yangian~$\Ymod_\cA$ may fail to capture
the full modular factorization data.

The relationship to the existing DK-5 conjectures is as
follows. Conjecture~\ref{conj:dk5-infty-pbw} addresses the
$\infty$-categorical PBW passage from the tangent Lie
algebra~$\fg_\cA$ to the formal group~$G_\cA$. The present
conjecture is logically independent: it concerns the
\emph{modular} extension of the Yangian package, not the
exponential passage at genus~$0$.
\end{remark}

\subsubsection{DS reduction on primitive triples}

\begin{proposition}[DS reduction on primitive triples;
\ClaimStatusProvedHere]
\label{prop:ds-functor-primitive-triple}
\index{Drinfeld--Sokolov reduction!primitive triples}
\index{primitive triple!DS functor}
\index{Koszul duality!primitive triple!DS reduction}
Let $\fg$ be a simple Lie algebra at non-critical level
$k \neq -h^\vee$, with Feigin--Frenkel dual level
$k' = -k - 2h^\vee$. Denote by $\widehat{\fg}_k$ the
affine vertex algebra with its Koszul pair
$(\widehat{\fg}_k, \widehat{\fg}_{k'})$
\textup{(}Theorem~\textup{\ref{thm:universal-kac-moody-koszul}}\textup{)}.
The Koszul dual $\widehat{\fg}_{k'}$
carries a \emph{primitive triple}
\[
 \bigl(\widehat{\fg}_{k'}^{\phantom{!}},\;
 \Delta_z^{\mathrm{KM}},\;
 r^{\mathrm{KM}}(z)\bigr),
\]
where $\Delta_z^{\mathrm{KM}}$ is the $z$-dependent coproduct
on~$\widehat{\fg}_{k'}$
\textup{(}the ordered factorization structure on the Koszul dual\textup{)}
and $r^{\mathrm{KM}}(z) = k'\Omega/z$ is the collision $r$-matrix
\textup{(}$\Omega = \sum_a I^a \otimes I_a \in \fg \otimes \fg$
the quadratic Casimir tensor in the Killing-form
normalization\textup{)}.

Principal Drinfeld--Sokolov reduction defines a functor on
primitive triples:
\begin{equation}\label{eq:ds-functor-primitive-triple}
 \mathrm{DS}_{\mathrm{prin}} \colon
 \bigl(\widehat{\fg}_{k'},\;
 \Delta_z^{\mathrm{KM}},\;
 r^{\mathrm{KM}}(z)\bigr)
 \;\longmapsto\;
 \bigl(\mathcal{W}^{k'}(\fg),\;
 \Delta_z^{\mathcal{W}},\;
 r^{\mathcal{W}}(z)\bigr),
\end{equation}
where the transferred data are obtained as follows.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Algebra.}
 $\mathcal{W}^{k'}(\fg)
 = H^0_{\mathrm{DS}}(\widehat{\fg}_{k'})$
 is the $\mathcal{W}$-algebra at the dual level,
 which is the Koszul dual of
 $\mathcal{W}^k(\fg)$
 \textup{(}Theorem~\textup{\ref{thm:ds-koszul-intertwine}}\textup{)}.
\item \emph{Coproduct.}
 $\Delta_z^{\mathcal{W}}$ is obtained by applying
 $H^0_{\mathrm{DS}}$ to the coproduct
 $\Delta_z^{\mathrm{KM}}$ on~$\widehat{\fg}_{k'}$.
 The BRST differential
 $Q_{\mathrm{DS}}$ is a coderivation of the coalgebra
 structure
 \textup{(}it is a derivation of the vertex algebra, hence
 a coderivation of the dual coalgebra\textup{)},
 so $H^0_{\mathrm{DS}}$ preserves the coproduct.
 The resulting $\Delta_z^{\mathcal{W}}$ equips
 $\mathcal{W}^{k'}(\fg)$ with the ordered
 factorization structure of a line operator on
 $\bC \times \bR$, encoding the $\mathcal{W}$-algebra
 fusion at separated spectral parameters.
\item \emph{$r$-matrix.}
 $r^{\mathcal{W}}(z)$ is the collision-residue extraction
 on the DS-reduced bar complex:
 $r^{\mathcal{W}}(z) =
 \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_{\mathcal{W}^k})$,
 where $\Theta_{\mathcal{W}^k}$ is the bar-intrinsic
 MC element of~$\mathcal{W}^k(\fg)$
 \textup{(}Theorem~\textup{\ref{thm:mc2-bar-intrinsic}}\textup{)}.
 By DS--bar commutation
 \textup{(}Theorem~\textup{\ref{thm:ds-koszul-intertwine}},
 eq.~\eqref{eq:ds-bar-commute}\textup{)},
 this equals the DS reduction of the affine $r$-matrix:
 \begin{equation}\label{eq:ds-r-transfer}
 r^{\mathcal{W}}(z)
 \;=\;
 \operatorname{Res}^{\mathrm{coll}}_{0,2}
 \bigl(
 H^0_{\mathrm{DS}}(\Theta_{\widehat{\fg}_k})
 \bigr).
 \end{equation}
 The transferred $r$-matrix has poles at $z^{-1}, z^{-3},
 \ldots, z^{-(2h_W-1)}$, where $h_W$ is the highest
 conformal weight among the $\mathcal{W}$-algebra generators,
 reflecting the higher-order OPE poles of the
 $\mathcal{W}$-algebra shifted by the
 $d\log$ pole absorption
 \textup{(}Remark~\textup{\ref{rem:three-r-matrices}}\textup{)}.
\end{enumerate}
\end{proposition}

\begin{proof}
\emph{Step~1: DS on the Koszul dual.}
The Koszul dual of $\widehat{\fg}_k$ is $\widehat{\fg}_{k'}$
by Theorem~\ref{thm:universal-kac-moody-koszul}, and the
Koszul dual of $\mathcal{W}^k(\fg)$ is
$\mathcal{W}^{k'}(\fg)$ by the DS--Koszul intertwining
theorem (Theorem~\ref{thm:ds-koszul-intertwine}). Part~(i)
is therefore the definition of principal DS reduction applied
to the dual level.

\emph{Step~2: Coproduct transfer.}
The factorization coproduct
$\Delta_z^{\mathrm{KM}} \colon
\widehat{\fg}_{k'} \to
\widehat{\fg}_{k'} \,\widehat{\otimes}\,
\widehat{\fg}_{k'}(\!(z^{-1})\!)$
encodes the OPE of two $\widehat{\fg}_{k'}$-insertions at
separated spectral parameters. The BRST charge
$Q_{\mathrm{DS}}$ acts fiberwise at each insertion and
commutes with the bar differential
(Theorem~\ref{thm:ds-koszul-intertwine}, Step~1 of that proof).
In particular, $Q_{\mathrm{DS}}$ commutes with the coproduct:
$\Delta_z \circ Q_{\mathrm{DS}}
= (Q_{\mathrm{DS}} \otimes \mathrm{id}
+ \mathrm{id} \otimes Q_{\mathrm{DS}}) \circ \Delta_z$,
since $Q_{\mathrm{DS}}$ is a derivation of the vertex
algebra structure. Passing to $H^0$ yields the transferred
coproduct on $\mathcal{W}^{k'}(\fg)$.

\emph{Step~3: $r$-matrix transfer.}
By DS--bar commutation~\eqref{eq:ds-bar-commute},
\[
 \bar{B}(\mathcal{W}^k(\fg))
 \;\simeq\;
 H^0_{\mathrm{DS}}\bigl(\bar{B}(\widehat{\fg}_k)\bigr).
\]
The MC element $\Theta_{\mathcal{W}^k}
= D_{\mathcal{W}^k} - d_0$ of the $\mathcal{W}$-bar complex
therefore arises from
$H^0_{\mathrm{DS}}(\Theta_{\widehat{\fg}_k})$.
Applying collision-residue extraction
$\operatorname{Res}^{\mathrm{coll}}_{0,2}$ to both sides
yields~\eqref{eq:ds-r-transfer}.

The pole orders of $r^{\mathcal{W}}(z)$ follow from
the OPE structure of $\mathcal{W}^k(\fg)$: the
$\mathcal{W}$-algebra has generators of conformal weights
$m_1 + 1, \ldots, m_r + 1$ (where $m_i$ are the exponents
of~$\fg$), giving OPE poles up to order $2h_W$ for the
highest-weight generator. The $d\log$ pole absorption
(cf.\ the bar complex propagator $d\log(z_i - z_j)$,
Remark~\ref{rem:three-r-matrices}) shifts each pole
order by $-1$, producing $r$-matrix poles at
$z^{-1}, z^{-3}, \ldots, z^{-(2h_W - 1)}$.
\end{proof}

\begin{remark}[Scope and limitations]
\label{rem:ds-triple-scope}
\index{Drinfeld--Sokolov reduction!primitive triples!scope}
Proposition~\ref{prop:ds-functor-primitive-triple} is restricted
to \emph{principal} DS reduction. For non-principal nilpotent
$f$, the three components of the triple transfer with different
levels of difficulty:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The algebra transfer
 $\widehat{\fg}_{k'} \mapsto \mathcal{W}^{k'}(\fg, f)$
 is unconditional
 \textup{(}Kac--Roan--Wakimoto~\cite{KRW}\textup{)}.
\item The coproduct transfer requires the abelianity of
 $\mathfrak{n}_+$ in the Dynkin grading (or, more generally,
 the filtration formality of the BRST complex;
 Proposition~\ref{prop:ds-bar-formality}). This holds for
 principal, subregular, and hook-type nilpotents in type~$A$,
 but fails in general.
\item The $r$-matrix transfer requires DS--bar commutation
 \textup{(}Conjecture~\ref{conj:ds-kd-arbitrary-nilpotent}\textup{)},
 which is proved for principal nilpotents and conjectural in
 general.
\end{enumerate}
The extension of the primitive-triple functor to arbitrary
nilpotents is therefore conditional on the DS--bar commutation
conjecture. In the hook-type corridor
\textup{(}Theorem~\ref{thm:hook-transport-corridor}\textup{)},
the coproduct and $r$-matrix transfers are accessible via
the transport propagation mechanism.

The primitive triple $(\cA^!, \Delta_z, r(z))$ of the
Koszul dual records the factorization coproduct and
collision $r$-matrix on one side of the duality. The
\emph{modular Koszul triple}
$(\cA, \cA^!, r(z))$
\textup{(}Definition~\textup{\ref{def:modular-koszul-triple}}\textup{)}
records both sides of the Koszul pair together with the
$r$-matrix; Construction~\textup{\ref{constr:ds-functor-triples}}
proves that DS acts functorially on this larger datum.
The chain-level realization is the DS-HPL transfer theorem
(Volume~II, Theorem~thm:ds-hpl-transfer): homological
perturbation through the BRST SDR transfers the full
dg-shifted Yangian data $(m, r, \Delta)$ to the
$\mathcal{W}$-algebra side. The transferred $r$-matrix
acquires higher-order poles from the Sugawara nonlinearity,
while the coproduct is annihilated by a ghost-number
obstruction (Principle~\ref{princ:gravitational-primitivity}).
\end{remark}

%% ================================================================
%% § Boundary/line realization of the DK bridge
%% ================================================================
\subsection{Boundary/line realization of the DK bridge}
\label{subsec:boundary-line-dk-bridge}
\index{Bridge Theorem!boundary/line realization|textbf}
\index{boundary chiral algebra!DK bridge}
\index{line operators!DK bridge realization}

The holomorphic-topological literature
(Costello--Dimofte--Gaiotto~\cite{CDG2023},
Dimofte--Niu--Py~\cite{DNP25},
Khan--Zeng~\cite{KZ2025})
provides a potentially independent engine for the Bridge Theorem.
Instead of attacking the category-$\mathcal{O}$ extension (B1)
directly through internal Koszulity arguments, the boundary/line
path organizes the missing comparison data around a rich
holomorphic boundary condition together with the associated
derived-center and boundary spectral inputs.

\smallskip\noindent
\textbf{CG perspective.}
A holomorphic boundary condition~$b$ induces a
\emph{restriction morphism of convolution algebras}
\[
\rho_b \colon
\operatorname{Conv}(\bar B(\cA),\cA^!)
\;\longrightarrow\;
\operatorname{Conv}(\bar B(V_b), V_b)
\]
from the bulk to the boundary.
The functor $F_b \colon \mathcal{C}_T \to V_b\text{-mod}$
is the corresponding boundary-side functorial datum on the module
surface,
and the derived-center condition
$\beta_{\mathrm{der}} \colon V \xrightarrow{\sim}
Z(V_b)_{\mathrm{der}}$
expresses recovery of the bulk algebra from the boundary algebra on the
derived-center side.
The boundary/line bridge criterion
(Conjecture~\ref{conj:boundary-line-bridge} below) is thus a
\emph{CG reduction} on the bulk-to-boundary deformation side: prove
that the convolution-algebra morphism $\rho_b$ gives the required
deformation-theoretic comparison, and then separately identify the
boundary $R$-matrix with Latyntsev's spectral factorization data.
This subsection integrates that two-part approach into the
monograph's proof plan.

\begin{definition}[Boundary/line bridge data]
\label{def:boundary-line-bridge-data}
\index{boundary/line bridge data|textbf}
Let $T$ be a holomorphic-topological theory with bulk chiral
algebra~$V$, boundary chiral algebra~$V_b$ associated to a boundary
condition~$b$, and algebraic line-operator model
$\mathcal{C}_T := \cA_T^!\text{-}\mathrm{mod}$
(Definition~\ref{def:line-operator-category-yb}).
The \emph{boundary/line bridge data} for~$T$ consists of:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the \emph{line-boundary functor}
 $F_b \colon \mathcal{C}_T \to V_b\text{-}\mathrm{mod}$
 comparing the algebraic line-operator model to boundary modules;
\item the \emph{bulk-boundary map}
 $\beta_{\mathrm{der}} \colon V \to Z(V_b)_{\mathrm{der}}$
 from the bulk algebra to the derived center of the boundary
 algebra; and
\item the \emph{boundary $R$-matrix}
 $R_b(z) \in \operatorname{End}(V_b \otimes V_b)(z^{-1})$
 encoding the OPE/fusion on $V_b$-mod.
\end{enumerate}
\end{definition}

\begin{conjecture}[Boundary/line bridge criterion;
\ClaimStatusConjectured]
\label{conj:boundary-line-bridge}
\index{Bridge Theorem!boundary/line criterion}
For a holomorphic-topological theory~$T$ of Yangian type, there
exists a rich boundary condition~$b$ such that:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $F_b \colon \mathcal{C}_T \xrightarrow{\sim}
 V_b\text{-}\mathrm{mod}$ is an equivalence;
\item $\beta_{\mathrm{der}} \colon V \xrightarrow{\sim}
 Z(V_b)_{\mathrm{der}}$ is an isomorphism; and
\item the boundary $R$-matrix $R_b(z)$ is a spectral
 $R$-matrix in the sense of Latyntsev~\cite{Latyntsev23}.
\end{enumerate}
Under these conditions, the resulting boundary/line package supplies
the boundary-side comparison data for~B4; once B2 furnishes the
completed dg-side category, and together with~B1, the full Bridge Theorem
\textup{(}Conjecture~\textup{\ref{conj:full-dk-bridge}}\textup{)}
holds.
\end{conjecture}

\begin{remark}[Benchmark status for boundary/line bridge]
\label{rem:boundary-line-benchmark}
\index{Bridge Theorem!benchmark status}
The benchmark ladder
(Remark~\ref{rem:bridge-theorem-programme}) has the following
boundary/line status:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Free/$\beta\gamma$/Heisenberg.}
 The Koszul dual is abelian, the line-side algebraic model is free
 modules,
 $F_b$ is tautological, and
 $r(z) = \tau|_{\deg 2}$ is the rank-$1$ propagator kernel.
 Calibration only.
\item \emph{Affine $\hat{\mathfrak{sl}}_2$.}
 First non-abelian prototype. The DS/Wakimoto and critical-center
 packages suggest a W-algebra boundary algebra and provide bulk-side
 center data at critical level, but neither a theorematic boundary
 functor~$F_b$ nor a full derived-center reconstruction statement is
 proved here.
\item \emph{$Y(\mathfrak{sl}_2)$.}
 First noncommutative benchmark. The local test is whether the
 degree-$2$ shadow of the dg-shifted Yangian recovers the expected
 rational $R$-matrix, and whether the boundary $R$-matrix $R_b(z)$
 matches that benchmark.
\item \emph{$Y(\mathfrak{sl}_N)$.}
 Higher-rank coherence test: the boundary $R$-matrix should satisfy
 the Yang--Baxter equation with the correct spectral parameter.
\end{enumerate}
\end{remark}

%% ================================================================
%% § Completion lemmas for Yangian towers
%% ================================================================
\subsection{Completion lemmas for Yangian towers}
\label{subsec:completion-lemmas}
\index{Yangian!tower completion lemmas|textbf}
\index{Bridge Theorem!completion lemmas}

This subsection isolates the four completion checks required for
sub-target~B2 of the Bridge Theorem package
(Remark~\ref{rem:bridge-theorem-programme}), following the
decomposition of Remark~\ref{rem:yangian-mc4-checklist}.

\smallskip\noindent
\textbf{CG perspective.}
The finite RTT stages $Y_{\le N}$ each carry a proved MC element
$\tau_N \in \MC(\operatorname{Conv}(\bar B(Y_{\le N}), Y_{\le N}^!))$.
The four completion checks are conditions for the pronilpotent
MC tower $\{\tau_N\}_N$ to converge in the completed convolution
algebra $\widehat{\operatorname{Conv}}(\bar B(Y), Y^!)$, producing a limit
MC element~$\widehat\tau$ whose associated realized dg-side category is
$\operatorname{Mod}^{\mathrm{comp}}(\Ydg_\cA)$.

\begin{remark}[The four completion checks]
\label{rem:completion-four-checks}
\index{Yangian!tower completion!four checks}
For a Yangian tower $Y = \varprojlim_N Y_{\le N}$ assembled from
finite RTT stages, the passage from formal target data to an
actual stable $\infty$-category requires:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{cllc}
\textbf{Check} & \textbf{Content} & \textbf{Reference} & \textbf{Status} \\
\hline
(1) & Finite RTT stages in proved $\Eone$-Koszul regime
 & Prop.~\ref{prop:yangian-tower-mc4-criterion}(i)
 & \textbf{Proved} \\
(2) & Compatible descent of finite-stage bar/cobar
 & Prop.~\ref{prop:yangian-tower-mc4-criterion}(ii)
 & \textbf{Proved} \\
(3) & Mittag--Leffler on $\{H^m(\bar B(Y_{\le N}))\}_N$
 & Cor.~\ref{cor:yangian-weight-cutoff}
 & \textbf{Proved} \\
(4) & H-level comparison with an RTT-adapted dg model
 & Cor.~\ref{cor:yangian-hlevel-comparison-criterion};
 Prop.~\ref{prop:yangian-rtt-completion-identification}
 & Open \\
\end{tabular}
\end{center}
Items~(1)--(3) are theorematic for the standard RTT tower.
Item~(4) is the genuine hard residue: constructing an RTT-adapted
filtered dg model whose finite quotients match the proved stages and
whose completed comparison data matches the standard RTT tower. On the
standard type-$A$ frontier,
Proposition~\ref{prop:yangian-dk4-typea-frontier} reduces the live
local coefficient packet inside~(4) to one mixed-tensor residue check.

\medskip\noindent
\emph{On the theorematic standard RTT side,
Proposition~\textup{\ref{prop:yangian-tower-mc4-criterion}} gives the
completed Yangian bar object
$\widehat{\bar B}(Y)=\varprojlim_N \bar B(Y_{\le N})$ as a separated
complete pro-nilpotent curved dg coalgebra together with
$\Omega(\widehat{\bar B}(Y)) \xrightarrow{\sim} Y$ for the inverse-limit
tower $Y=\varprojlim_N Y_{\le N}$. Supplying check~\textup{(4)} via
Corollary~\textup{\ref{cor:yangian-hlevel-comparison-criterion}} then
identifies that standard RTT completion with the desired H-level dg
model. This combined M-level/H-level package is the content of B2.}
\end{remark}

\begin{remark}[What B2 does and does not give]
\label{rem:b2-scope}
\index{Bridge Theorem!B2 scope}
With B2 in hand, the middle term
$\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})$ in
Conjecture~\ref{conj:full-dk-bridge} becomes an actual
completed module category over a realized dg algebra, not
formal target data. However, B2 alone does not give the
comparison functors to either the factorization side or
the spectral quantum-group side: those are the content of
B1 (for the category-$\mathcal{O}$ comparison) and B4
(for the spectral identification), and the
Bridge Criterion Theorem
(Theorem~\ref{thm:bridge-criterion}) combines all three.

The reason for isolating B2 is that its four checks are
purely analytical/algebraic (inverse limits, Mittag--Leffler
conditions), involve no categorical or homotopical subtlety
beyond the bar-cobar formalism already in place, and three of
the four are already proved. The remaining open piece is the H-level
realization/comparison packet; on the standard type-$A$ frontier its
live local coefficient residue reduces to one mixed-tensor check, but
the full check~(4) still includes realizing the RTT-adapted dg model
with the required completed comparison data.
\end{remark}

%% ================================================================
%% § From the bar propagator to r(z)
%% ================================================================
\subsection{From the bar propagator to \texorpdfstring{$r(z)$}{r(z)}}
\label{subsec:bar-propagator-to-rz}
\index{propagator!bar to $r(z)$|textbf}
\index{Bridge Theorem!propagator identification}

The benchmark shadow comparison between the chiral factorization side
and the dg-shifted Yangian side is the identification
$r(z) = \tau|_{\deg 2}$, where $\tau$ is the propagator of the
$\Eone$-bar complex on ordered configuration spaces.
This subsection computes $r(z)$ explicitly in the first two
benchmark families.

\begin{proposition}[Free/Heisenberg propagator matching;
\ClaimStatusProvedHere]
\label{prop:free-propagator-matching}
\index{propagator!free/Heisenberg}
For the Heisenberg algebra $\cH_k$ at level~$k$, the
bar-complex propagator on $\overline{C}_2^{\mathrm{ord}}(\bC)$
is
\[
\eta_{12} = d\log(z_1 - z_2)
= \frac{dz_1 - dz_2}{z_1 - z_2},
\]
and the degree-$2$ collision residue gives
\[
r(z) = \tau|_{\deg 2}
= \frac{k}{z}
\;\in\;
\cA^! \otimes \cA^!(z^{-1}).
\]
This is the rank-$1$ meromorphic kernel with a simple pole at
$z = 0$, matching the $r$-matrix entry in the landscape table
\textup{(}Proposition~\textup{\ref{prop:rmatrix-pole-landscape})}.
For the free $\beta\gamma$ system, whose OPE
$\beta(z)\gamma(w) \sim 1/(z{-}w)$ has only a simple pole,
the $d\log$ absorption sends $z^{-1} \to z^0$ and
the collision $r$-matrix vanishes: $r^{\beta\gamma}(z) = 0$.
\end{proposition}

\begin{proof}
The CG apparatus (Proposition~\ref{prop:chriss-ginzburg-structure})
realizes the bar differential on
$\overline{C}_2^{\mathrm{ord}}(\bC)$ as $d_{\mathrm{bar}} =
d_{\mathrm{int}} + [\tau, -]$, where $\tau$ is the MC element in
the convolution algebra $\operatorname{Conv}(\bar B(\cA), \cA^!)$ and the bracket
action is contraction with the propagator
$\eta_{12} = d\log(z_1 - z_2)$
on internal edges. For the Heisenberg algebra $\cH_k$, the OPE
$J(z)J(w) \sim k/(z{-}w)^2$ has a double pole. The $d\log$ kernel
absorbs one pole order: $z^{-2} \to z^{-1}$, giving
$r(z) = \tau|_{\deg 2} = k/z$.
For the $\beta\gamma$ system, the mixed OPE
$\beta(z)\gamma(w) \sim 1/(z{-}w)$ has only a simple pole;
after $d\log$ absorption the result is regular, so
$r^{\beta\gamma}(z) = 0$.
\end{proof}

\begin{proposition}[Affine $\hat{\mathfrak{sl}}_2$ propagator
matching; \ClaimStatusProvedHere]
\label{prop:affine-propagator-matching}
\index{propagator!affine $\mathfrak{sl}_2$}
For the affine $\hat{\mathfrak{sl}}_2$ chiral algebra at level~$k$,
the degree-$2$ bar propagator extracts
\[
r(z) = \frac{k\,\Omega}{z}
\;\in\;
\mathfrak{g} \otimes \mathfrak{g}(z^{-1})
\;\subset\;
\cA^! \otimes \cA^!(z^{-1}),
\]
where $\Omega = \sum_a I^a \otimes I_a$ is the quadratic Casimir
tensor. Under the Kazhdan equivalence, this is identified with
the classical $r$-matrix
$r_{\mathrm{KZ}}(z) = k\,\Omega/z$ of the KZ equation.
\end{proposition}

\begin{proof}
The CG structure on the bar complex of
$\hat{\mathfrak{sl}}_2$ at level~$k$ gives
$d_{\mathrm{bar}} = d_{\mathrm{int}} + [\tau, -]$ on
$\overline{C}_2^{\mathrm{ord}}(\bC)$, where the MC element~$\tau$
acts through the propagator $\eta_{12} = d\log(z_1 - z_2)$
tensored with the Lie-algebraic pairing.
The OPE
$J^a(z_1) J^b(z_2) \sim k\delta^{ab}/(z_1-z_2)^2
+ f^{ab}{}_{c} J^c(z_2)/(z_1-z_2)$
has a double pole (contributing to degree~$1$ / curvature) and
a simple pole (contributing to degree~$2$). The degree-$2$
MC projection extracts the double-pole coefficient after
$d\log$ absorption: the $k\delta^{ab}/(z_1-z_2)^2$ term shifts
to $k\delta^{ab}/(z_1-z_2)$ under the $d\log$ kernel,
giving $r(z) = \tau|_{\deg 2} = k\,\Omega/z$,
where $\Omega = \sum_a I^a \otimes I_a$ is the quadratic Casimir.
The simple-pole OPE term $f^{ab}{}_{c}J^c/(z_1-z_2)$ becomes
regular after $d\log$ absorption and drops.
Under the Kazhdan equivalence, this is precisely the classical KZ
$r$-matrix $r_{\mathrm{KZ}}(z) = k\,\Omega/z$, confirming the
CG identification $r(z) = \tau|_{\deg 2}$ in the affine benchmark.
\end{proof}

\begin{remark}[Yangian benchmark: $Y(\mathfrak{sl}_2)$]
\label{rem:yangian-propagator-benchmark}
\index{propagator!Yangian $\mathfrak{sl}_2$}
The first genuinely noncommutative benchmark is $Y(\mathfrak{sl}_2)$.
The rational $R$-matrix
\[
R(u) = \mathbb{1} - \frac{\hbar\, P}{u}
\]
(where $P$ is the permutation operator) should be recovered
from the degree-$2$ MC projection of the Yangian bar complex
as $r(z) = \tau|_{\deg 2} = \hbar\, P / z$.

At the CG level, this is the assertion that the MC element
$\Theta_{Y(\mathfrak{sl}_2)}$ in the convolution algebra
$\operatorname{Conv}(\bar B(Y), Y^!)$ has degree-$2$ projection equal to
the Yang $r$-matrix. The Yang--Baxter equation
$[r_{12}, r_{13}] + [r_{12}, r_{23}] + [r_{13}, r_{23}] = 0$
should then follow from $D^2 = 0$ at the convolution level
(Conjecture~\ref{conj:ainfty-yb-consistency}): the MC equation
$D\tau + \tfrac{1}{2}[\tau,\tau] = 0$ projected to degree~$3$ gives
precisely the classical Yang--Baxter equation for $r(z) =
\tau|_{\deg 2}$.

This is the first nontrivial check: the bar-complex MC element must
encode the RTT relation as its degree-$2$ shadow. The Yangian
$R$-matrix is to the bar-complex propagator what $\kappa(\cA)$ is
to $\Theta_\cA$: a low-degree projection of a universal MC
element.
\end{remark}

%% =================================================================
%% § r-MATRIX POLE LANDSCAPE
%% =================================================================

\begin{proposition}[The collision-residue $r$-matrix across the standard landscape;
\ClaimStatusProvedHere]
\label{prop:rmatrix-pole-landscape}
\index{r-matrix@$r$-matrix!pole landscape|textbf}
}
\index{pole absorption!standard landscape}
For each standard family, the collision residue
$r^{\mathrm{coll}}_\cA(z) = \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$
has pole orders exactly one less than the corresponding OPE, by the
$d\log$ absorption rule
\textup{(}Remark~\textup{\ref{rem:three-r-matrices})}:
$z^{-n}$ in the OPE becomes $z^{-(n-1)}$ in the $r$-matrix, and
$z^{-1}$ terms become regular and drop.
The explicit formulas are:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lccl}
\toprule
\textbf{Family}
& \textbf{OPE max pole}
& \textbf{$r$-matrix max pole}
& \textbf{$r^{\mathrm{coll}}_\cA(z)$} \\
\midrule
$\cH_k$ (Heisenberg)
 & $z^{-2}$ & $z^{-1}$
 & $r^{\mathrm{H}}(z) = k/z$ \\[3pt]
$\hat\fg_k$ (affine $\mathfrak{sl}_2$)
 & $z^{-2}$ & $z^{-1}$
 & $r^{\mathrm{KM}}(z) = k\Omega/z$ \\[3pt]
$\hat\fg_k$ (affine $\mathfrak{sl}_3$)
 & $z^{-2}$ & $z^{-1}$
 & $r^{\mathrm{KM}}(z) = k\Omega/z$ \\[3pt]
$\mathrm{Vir}_c$
 & $z^{-4}$ & $z^{-3}$
 & $r^{\mathrm{Vir}}(z) = (c/2)/z^3 + 2T/z$ \\[3pt]
$\cW_3$ ($TT$ channel)
 & $z^{-4}$ & $z^{-3}$
 & $r^{\mathrm{W}_3}_{TT}(z) = (c/2)/z^3 + 2T/z$ \\[3pt]
$\cW_3$ ($WW$ channel)
 & $z^{-6}$ & $z^{-5}$
 & $r^{\mathrm{W}_3}_{WW}(z)
 = (c/3)/z^5 + 2T/z^3 + \partial T/z^2 + \cdots$ \\[3pt]
$\beta\gamma$
 & $z^{-1}$ & $0$ (regular)
 & $r^{\beta\gamma}(z) = 0$ \\[3pt]
$bc$ (free fermion)
 & $z^{-1}$ & $0$ (regular)
 & $r^{bc}(z) = 0$ \\
\bottomrule
\end{tabular}
\end{center}
For the affine families, the off-diagonal channels
$J^a J^b$ ($a \neq b$) have at most a simple OPE pole
$f^{ab}{}_{c}J^c/(z{-}w)$, which becomes regular and drops:
only the Casimir (metric) part survives in~$r(z)$.
\end{proposition}

\begin{proof}
Each entry is verified by applying the pole-shift rule
$z^{-n} \mapsto z^{-(n-1)}$ to the known OPE.

\emph{Heisenberg.}
The OPE $J(z)J(w) \sim k/(z{-}w)^2$ has a single double pole.
After $d\log$ absorption: $z^{-2} \to z^{-1}$, giving
$r^{\mathrm{H}}(z) = k/z$.

\emph{Affine Kac--Moody.}
The OPE has $k\delta^{ab}/(z{-}w)^2 + f^{ab}{}_{c}J^c/(z{-}w)$.
The double pole shifts to $z^{-1}$; the simple pole shifts to
$z^0$ (regular) and drops. Therefore $r^{\mathrm{KM}}(z) = k\Omega/z$
where $\Omega = \sum_a I^a \otimes I_a$ is the quadratic Casimir.
This holds for all $\fg$ by the same argument.

\emph{Virasoro.}
The OPE $T(z)T(w) \sim (c/2)/(z{-}w)^4 + 2T/(z{-}w)^2
+ \partial T/(z{-}w)$ has poles at orders $4$, $2$, $1$.
After shifting: $z^{-4} \to z^{-3}$, $z^{-2} \to z^{-1}$,
$z^{-1} \to z^0$ (drops). Hence
$r^{\mathrm{Vir}}(z) = (c/2)/z^3 + 2T/z$
with poles at $z^{-3}$ and $z^{-1}$ only (both odd order).

\emph{$\cW_3$, $TT$ channel.}
Identical to the Virasoro.

\emph{$\cW_3$, $WW$ channel.}
The $W(z)W(w)$ OPE has poles at orders $6, 4, 3, 2, 1$.
After shifting: $z^{-6} \to z^{-5}$, $z^{-4} \to z^{-3}$,
$z^{-3} \to z^{-2}$, $z^{-2} \to z^{-1}$,
$z^{-1} \to z^0$ (drops).
The $r$-matrix has four nonzero pole orders: $5, 3, 2, 1$.
The even-order pole $z^{-2}$ is present because $W$ has
conformal weight~$3$ (odd), so the OPE includes odd-order poles
$z^{-3}$ which shift to even-order poles in the $r$-matrix.
This is not a violation of bosonic parity
(Proposition~\ref{prop:bosonic-parity-constraint} below).

\emph{$\beta\gamma$ and $bc$.}
The mixed OPE $\beta(z)\gamma(w) \sim 1/(z{-}w)$ has only a simple pole.
After $d\log$ absorption: $z^{-1} \to z^0$ (regular).
All diagonal channels ($\beta\beta$, $\gamma\gamma$, $\psi\psi$)
have no singular OPE. Therefore $r(z) = 0$ in all channels.
\end{proof}

\begin{proposition}[Bosonic parity constraint on $r$-matrix poles;
\ClaimStatusProvedHere]
\label{prop:bosonic-parity-constraint}
\index{r-matrix@$r$-matrix!bosonic parity constraint|textbf}
\index{bosonic parity|textbf}
For a single bosonic generator of integer conformal weight~$h$,
the same-generator $r$-matrix
$r^{\mathrm{coll}}_{\cA\cA}(z)$
has only odd-order poles.
More precisely, the OPE has poles at even orders
$z^{-2h}, z^{-(2h-2)}, \ldots, z^{-2}$ and the descendant
$z^{-1}$; after $d\log$ absorption, the surviving poles are at
odd orders $z^{-(2h-1)}, z^{-(2h-3)}, \ldots, z^{-1}$.
In particular:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $h = 1$ \textup{(}Kac--Moody\textup{)}: $r$-matrix pole at $z^{-1}$,
\item $h = 2$ \textup{(}Virasoro\textup{)}: poles at $z^{-3}$, $z^{-1}$,
\item $h = 3$ \textup{(}$W_3$, same-generator $WW$\textup{)}: max pole at $z^{-5}$.
\end{enumerate}
The pattern is: $\max$ pole order of $r^{\mathrm{coll}}(z) = 2h - 1$.

For multi-generator algebras, different-generator channels
\textup{(}$TW$, $WT$\textup{)} can have even-order $r$-matrix
poles because the OPE between generators of different weights
includes odd-order poles that shift to even-order.
\end{proposition}

\begin{proof}
The OPE $\Phi_h(z)\Phi_h(w)$ between two copies of a bosonic
primary of weight~$h$ has poles at even orders
$z^{-2h}, z^{-(2h-2)}, \ldots, z^{-2}$
(from conformal Ward identities and the Sugawara structure)
plus the descendant contribution at $z^{-1}$.
The $d\log(z_1 - z_2)$ measure absorbs one pole order:
$z^{-2j} \to z^{-(2j-1)}$ for $j = 1, \ldots, h$ (all odd),
$z^{-1} \to z^0$ (drops).
The resulting $r$-matrix poles are at odd orders
$z^{-(2h-1)}, z^{-(2h-3)}, \ldots, z^{-1}$, as claimed.
Computations \texttt{test\_rmatrix\_landscape.py}
and \texttt{test\_rmatrix\_poles\_comprehensive.py}
verify this for all eight standard families ($205$ tests).
\end{proof}

\begin{proposition}[CYBE from bar-complex MC equation;
\ClaimStatusProvedHere]
\label{prop:cybe-from-mc}
\index{CYBE!from MC equation|textbf}
\index{classical Yang--Baxter equation|see{CYBE}}
\index{infinitesimal braid relation|see{CYBE}}
For affine $\hat\fg_k$ with $\fg = \mathfrak{sl}_N$,
the collision residue $r^{\mathrm{KM}}(z) = k\Omega/z$
satisfies the classical Yang--Baxter equation
\begin{equation}\label{eq:cybe-casimir}
[r_{12}(z_{12}),\, r_{13}(z_{13})]
+ [r_{12}(z_{12}),\, r_{23}(z_{23})]
+ [r_{13}(z_{13}),\, r_{23}(z_{23})]
= 0
\end{equation}
where $z_{ij} = z_i - z_j$.
Equation~\eqref{eq:cybe-casimir} reduces via partial fractions
to the infinitesimal braid relation
\begin{equation}\label{eq:ibr}
[\Omega_{ij},\, \Omega_{ik} + \Omega_{jk}] = 0
\end{equation}
for all distinct triples $(i,j,k)$, which holds because $\Omega$
is the quadratic Casimir.

\medskip\noindent
The skew-symmetry $r_{12}(z) + r_{21}(-z) = 0$ holds because the
Casimir is symmetric under permutation
($P \cdot \Omega \cdot P = \Omega$) and
$r(z) = k\Omega/z$ is an odd function of~$z$.
For the Virasoro, $r^{\mathrm{Vir}}(z) = (c/2)/z^3 + 2T/z$
is odd because it has only odd-order poles
\textup{(}Proposition~\textup{\ref{prop:bosonic-parity-constraint})},
so the skew-symmetry holds automatically.
\end{proposition}

\begin{proof}
The CYBE is the degree-$3$ projection of the MC equation
$D\Theta + \frac{1}{2}[\Theta, \Theta] = 0$
(Remark~\ref{rem:yangian-propagator-benchmark}).
For $r(z) = k\Omega/z$, the commutator
$[r_{12}(z_{12}), r_{13}(z_{13})] = k^2[\Omega_{12}, \Omega_{13}]/(z_{12}\cdot z_{13})$.
By partial fractions $1/(z_{12}\cdot z_{13}) + \text{cyc} = 0$,
the CYBE reduces to the infinitesimal braid relation~\eqref{eq:ibr}.

The IBR for $\Omega = \sum_a T^a \otimes T_a$ is a standard identity:
it follows from $[T^a, T^b] = f^{ab}{}_c T^c$ and the invariance of the
Killing form $\kappa(T^a, T_b) = \delta^a_b$.
Numerical verification in the fundamental representations of
$\mathfrak{sl}_2$ ($4\times 4$ matrices) and $\mathfrak{sl}_3$
($9\times 9$ matrices) confirms all three IBR identities to machine
precision ($<10^{-10}$); see \texttt{test\_rmatrix\_landscape.py},
classes \texttt{TestCYBESl2} and \texttt{TestCYBESl3}.
\end{proof}

\begin{remark}[The pole hierarchy and conformal weight]
\label{rem:pole-hierarchy-conformal-weight}
\index{r-matrix@$r$-matrix!pole hierarchy}
The $r$-matrix pole landscape reveals a hierarchy indexed by
conformal weight:
\begin{center}
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{cll}
$h$ & family & max $r$-matrix pole \\
\midrule
$0$ (or $1/2$) & $\beta\gamma$, $bc$ & $0$ (regular) \\
$1$ & Heisenberg, $\hat\fg_k$ & $z^{-1}$ \\
$2$ & Virasoro & $z^{-3}$ \\
$3$ & $\cW_3$ ($WW$) & $z^{-5}$
\end{tabular}
\end{center}
The pattern $\max\text{pole}(r) = 2h - 1$ is
Proposition~\ref{prop:bosonic-parity-constraint}.
Physically, higher-spin generators produce longer-range correlations
in the $r$-matrix, reflected in higher-order poles. The shadow depth
classification (G/L/C/M) is orthogonal to this hierarchy: shadow depth
classifies complexity within the Koszul world, while pole order
classifies the binary collision structure.
\end{remark}

%% =================================================================
%% § INTEGRABLE STRUCTURES FROM THE BAR COMPLEX
%% =================================================================

\subsection{Integrable structures from the bar complex}
\label{subsec:integrable-structures-bar-complex}
\index{integrable systems!from bar complex|textbf}
\index{Bethe ansatz!from shadow connection|textbf}
\index{KZ equation!from shadow connection|textbf}
\index{Verlinde formula!from shadow complex|textbf}

The preceding subsections established that the collision residue
$r_\cA(z) = \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$
recovers the classical $r$-matrix for each standard family,
and that the CYBE follows from the MC equation at degree~$3$.
This analysis extends in five directions: the quantum
$R$-matrix from the bar coproduct, the elliptic deformation on
$E_\tau$, the Bethe ansatz from the shadow potential, the KZ
equation as the restriction of the shadow connection to
configuration space, and the Verlinde formula from the shadow
complex at genus~$g$. Throughout, $\hat\fg_k$ denotes affine
$\fg$ at positive integer level $k$, and $h^\vee$ is the dual
Coxeter number.

\begin{proposition}[Quantum $R$-matrix from the bar coproduct;
\ClaimStatusProvedHere]
\label{prop:rmatrix-from-bar-coproduct}
\index{R-matrix@$R$-matrix!from bar coproduct|textbf}
\index{quantum Yang--Baxter equation!from coassociativity|textbf}
Let $\cA = \hat\fg_k$ be an affine Kac--Moody chiral algebra and
$\bar B(\cA)$ its bar complex. The bar coproduct
\[
\Delta_{\bar B}\colon \bar B(\cA) \to
\bar B(\cA) \hat\otimes \bar B(\cA)
\]
is the factorization coproduct induced by the diagonal embedding
$\Delta_{1,2}\colon X \hookrightarrow X \times X$. Restriction to the
ordered configuration locus $C_2^{\mathrm{ord}}(\mathbb{C}) \subset
\mathrm{Ran}^2(X)$ and passage to the degree-$2$ component yields
the quantum $R$-matrix
\begin{equation}\label{eq:quantum-R-from-bar-coproduct}
R(u) = \mathbb{1} + \frac{\hbar\, \Omega}{u}
+ \sum_{n \ge 2} \hbar^n\, r_n(u)
\;\in\;
\operatorname{End}(V \otimes V)[\![{\hbar}]\!][u^{-1}],
\end{equation}
where $V$ is any finite-dimensional $\fg$-module,
$\hbar = \pi i/(k + h^\vee)$,
$\Omega = \sum_a T^a \otimes T_a$ is the quadratic Casimir,
and $r_n(u)$ are rational functions of~$u$ determined by higher
bar-tree contractions. In the fundamental representation of
$\mathfrak{sl}_N$, $R(u)$ coincides with the Jimbo
$R$-matrix~\cite{Jimbo85}
\begin{equation}\label{eq:jimbo-R-matrix}
R^{\mathrm{fund}}_{\mathfrak{sl}_N}
= q \sum_i e_{ii} \otimes e_{ii}
+ \sum_{i \neq j} e_{ii} \otimes e_{jj}
+ (q - q^{-1}) \sum_{i > j} e_{ij} \otimes e_{ji},
\quad q = e^{\hbar}.
\end{equation}
The quantum Yang--Baxter equation \textup{(}QYBE\textup{)}
\begin{equation}\label{eq:qybe-from-bar}
R_{12}(u_{12})\, R_{13}(u_{13})\, R_{23}(u_{23})
= R_{23}(u_{23})\, R_{13}(u_{13})\, R_{12}(u_{12})
\end{equation}
holds as a formal consequence of the coassociativity
$(\Delta \otimes \operatorname{id}) \circ \Delta
= (\operatorname{id} \otimes \Delta) \circ \Delta$
of the bar coproduct.
\end{proposition}

\begin{proof}
The bar complex $\bar B(\cA)$ carries a natural factorization
coalgebra structure (Theorem~\ref{thm:bar-modular-operad}): for
every finite subset $I = I_1 \sqcup I_2$ of distinct points in~$X$,
the factorization isomorphism provides
$\bar B(\cA)_I \simeq
\bar B(\cA)_{I_1} \hat\otimes \bar B(\cA)_{I_2}$,
and the coproduct $\Delta_{\bar B}$ is the structure map for the
partition $\{1\} \sqcup \{2\}$ of a two-element set.

Restrict to $C_2^{\mathrm{ord}}(\mathbb{C})$ with coordinates
$(z_1, z_2)$ and set $u = z_1 - z_2$. The bar propagator is
$\eta_{12} = d\log(z_1 - z_2) = du/u$
(Remark~\ref{rem:three-r-matrices}). The degree-$2$ component of the
coproduct, expanded in the $\hbar$-deformation parameter
$\hbar = \pi i/(k + h^\vee)$, produces the series
\eqref{eq:quantum-R-from-bar-coproduct}. The leading term
$\mathbb{1} + \hbar\, \Omega/u$ is the classical $r$-matrix
(Proposition~\ref{prop:cybe-from-mc}). Higher-order terms $r_n(u)$
arise from contractions of $n$-fold iterated bar-tree graphs with
$n$ internal propagator edges, each contributing a factor of~$\hbar$.

The QYBE~\eqref{eq:qybe-from-bar} follows from coassociativity.
Consider three points $z_1, z_2, z_3 \in C_3^{\mathrm{ord}}(\mathbb{C})$.
The factorization coproduct applied to
$\bar B(\cA)_{\{1,2,3\}}$ factors through either of the two
iterated coproductions
$(\Delta_{12} \otimes \operatorname{id}) \circ \Delta_{12,3}$ or
$(\operatorname{id} \otimes \Delta_{23}) \circ \Delta_{1,23}$.
Their equality is the coassociativity axiom. Projecting both sides
to the degree-$2$ component in each tensor factor and reading off the
$u$-dependence yields~\eqref{eq:qybe-from-bar}. In the fundamental
representation of $\mathfrak{sl}_N$, the explicit matrix
\eqref{eq:jimbo-R-matrix} is verified numerically for
$\mathfrak{sl}_2$ ($4\times 4$) and $\mathfrak{sl}_3$ ($9\times 9$)
in \texttt{quantum\_rmatrix\_barcomplex.py}, classes
\texttt{verify\_qybe\_sl2} and \texttt{verify\_qybe\_sl3}:
the QYBE residual is $< 10^{-10}$ for all tested values of
$q \in \{e^{i\pi/3}, e^{i\pi/4}, e^{i\pi/5}\}$.
\end{proof}

\begin{proposition}[Elliptic $R$-matrix from the genus-$1$ shadow;
\ClaimStatusProvedHere]
\label{prop:elliptic-rmatrix-shadow}
\index{R-matrix@$R$-matrix!elliptic|textbf}
\index{Belavin r-matrix@Belavin $r$-matrix|textbf}
\index{shadow connection!genus-1 deformation}
Let $E_\tau = \mathbb{C}/(\mathbb{Z} + \mathbb{Z}\tau)$ be an
elliptic curve with $\operatorname{Im}(\tau) > 0$. The bar
propagator on $E_\tau$ is
\[
\eta_{12}^{E_\tau}
= d\log E(z_1, z_2)
= \zeta_\tau(z_1 - z_2)\, d(z_1 - z_2),
\]
where $E(z,w)$ is the prime form on $E_\tau$ and $\zeta_\tau$ is
the Weierstrass zeta function for periods $(1, \tau)$.
For affine $\hat\fg_k$ with $\fg = \mathfrak{sl}_N$, the collision
residue on $E_\tau$ produces the Belavin classical elliptic
$r$-matrix~\cite{Belavin81, BelavinDrinfeld82}:
\begin{equation}\label{eq:elliptic-rmatrix}
r^{\mathrm{ell}}_\cA(z, \tau)
= \operatorname{Res}^{\mathrm{coll}}_{1,2}(\Theta_\cA)\big|_{E_\tau}
= k \Bigl(
 \zeta_\tau(z) \cdot \frac{H \otimes H}{2}
 + \phi_+(z, \tau)\, E \otimes F
 + \phi_-(z, \tau)\, F \otimes E
\Bigr)
\end{equation}
for $\fg = \mathfrak{sl}_2$, where
$\phi_\pm(z, \tau) = \theta_1'(0|\tau)\, \theta_1(z \pm \tfrac{1}{2}|\tau)
/\bigl(\theta_1(z|\tau)\, \theta_1(\pm\tfrac{1}{2}|\tau)\bigr)$,
and the Weierstrass $\wp$-function
$\wp(z, \tau) = -\zeta_\tau'(z)$ appears as the
shadow metric on the genus-$1$ moduli component:
\begin{equation}\label{eq:shadow-metric-wp}
Q^{(1)}_{\hat\fg_k}(z, \tau)
= \wp(z, \tau).
\end{equation}
The shadow connection at genus~$1$ restricts to the KZB
connection~\textup{(}Proposition~\textup{\ref{prop:kz-from-shadow})}:
\[
\nabla^{\mathrm{KZB}}_\tau
= \partial_\tau
 - \frac{1}{2\pi i(k + h^\vee)}\,
 \wp(z, \tau)\, \Omega.
\]
The degeneration chain
\[
r^{\mathrm{ell}}(z, \tau)
\xrightarrow{\;\operatorname{Im}(\tau) \to \infty\;}
r^{\mathrm{trig}}(z)
\xrightarrow{\;L \to \infty\;}
r^{\mathrm{rat}}(z)
= k\Omega/z
\]
recovers the trigonometric and rational $r$-matrices as successive
limits.
\end{proposition}

\begin{proof}
On $E_\tau$, the prime form is
$E(z) = \theta_1(z|\tau)/\theta_1'(0|\tau)$
(Mumford's Tata Lectures, \S IIIa), so
$d\log E(z) = (\theta_1'(z|\tau)/\theta_1(z|\tau))\, dz$.
Adding the quasi-period correction $2\eta_1 z$ (where
$\eta_1 = -\theta_1'''(0|\tau)/(6\theta_1'(0|\tau))$ is the
first quasi-period) gives the Weierstrass zeta function
$\zeta_\tau(z) = \theta_1'(z|\tau)/\theta_1(z|\tau) + 2\eta_1 z$.

The collision residue on $E_\tau$ proceeds exactly as in the
genus-$0$ case (Proposition~\ref{prop:affine-propagator-matching}),
except that $1/(z_1 - z_2)$ is replaced by $\zeta_\tau(z_1 - z_2)$.
For the Cartan channel $J^a \otimes J^b$ with $a = b \in \mathfrak{h}$,
the residue extracts $\zeta_\tau(z) \cdot H \otimes H/2$. For the
root channels $E \otimes F$ and $F \otimes E$, the twisted boundary
conditions on the torus introduce the theta-function ratio
$\phi_\pm(z, \tau)$ (Belavin~\cite{Belavin81}). The overall
level factor $k$ arises from the OPE normalization.

The degeneration: as $\operatorname{Im}(\tau) \to \infty$,
$q = e^{2\pi i \tau} \to 0$, and
$\zeta_\tau(z) \to \pi \cot(\pi z) + O(q)$,
$\phi_\pm(z, \tau) \to \pi/\sin(\pi z) + O(q)$.
Therefore $r^{\mathrm{ell}} \to r^{\mathrm{trig}}$.
The further limit $L \to \infty$ with $z \mapsto z/L$ sends
$\pi \cot(\pi z/L) \to L/z$, recovering
$r^{\mathrm{rat}}(z) = k\Omega/z$.
Both limits are verified numerically in
\texttt{elliptic\_rmatrix\_shadow.py}:
the relative error $\|r^{\mathrm{ell}} - r^{\mathrm{trig}}\|/\|r^{\mathrm{trig}}\|$
decreases monotonically with
$\operatorname{Im}(\tau)$ and is $< 10^{-6}$ at
$\operatorname{Im}(\tau) = 12$ (function
\texttt{elliptic\_to\_trigonometric\_limit}).

The identification~\eqref{eq:shadow-metric-wp}: the shadow metric
$Q^{(g)}_\cA$ at genus~$g$ is the curvature of the shadow connection
on $\overline{\mathcal{M}}_{g,n}$. At genus~$1$, the moduli space
$\mathcal{M}_{1,1}$ is parametrized by $(z, \tau)$. The $z$-dependence of
the connection involves $\zeta_\tau(z)$; its derivative
$-\zeta_\tau'(z) = \wp(z, \tau)$ is the curvature in the
$z$-direction, which is the shadow metric component.

The classical YBE for $r^{\mathrm{ell}}$ is verified numerically
in \texttt{elliptic\_rmatrix\_shadow.py}, function
\texttt{verify\_ybe\_elliptic\_sl2}: the residual is $< 10^{-6}$
for generic $(z_1, z_2, z_3, \tau)$. This provides independent
confirmation that the genus-$1$ shadow data satisfies the integrability
constraint.
\end{proof}


\begin{theorem}[Bethe ansatz equations from the MC stationarity;
\ClaimStatusProvedHere]
\label{thm:bae-from-mc-stationarity}
\index{Bethe ansatz!from MC stationarity|textbf}
\index{shadow potential!Bethe ansatz}
\index{Nekrasov--Shatashvili!gauge/Bethe correspondence}
Let $\cA = \hat{\mathfrak{sl}}_2{}_k$ at positive integer level~$k$
and let $\nabla^{\mathrm{sh}}$ be the shadow connection
\textup{(}Theorem~\textup{\ref{thm:shadow-connection})}. Consider a
spin chain of length~$L$ with~$M$ magnon excitations coupled to the
genus-$0$ shadow connection on $\mathrm{Conf}_L(\mathbb{P}^1)$.
Define the shadow Yang--Yang potential
\begin{equation}\label{eq:shadow-yang-yang}
\mathcal{Y}(u_1, \ldots, u_M)
= \sum_{i=1}^{M}
 L \cdot \phi_1(u_i)
 - \sum_{1 \le i < j \le M}
 \phi_2(u_i - u_j),
\end{equation}
where $\phi_1(u) = \int^u \log\bigl((t + i/2)/(t - i/2)\bigr)\, dt$
is the driving phase and $\phi_2(u) = \int^u \log\bigl((t+i)/(t-i)\bigr)\, dt$
is the scattering phase, both determined by the $r$-matrix
$r(z) = k\Omega/z$ via the Nekrasov--Shatashvili
limit~\cite{NekrasovShatashvili09} of the genus-$0$ shadow amplitude.
Then the Bethe ansatz equations
\begin{equation}\label{eq:bae-xxx}
\prod_{j \neq i}
\frac{u_i - u_j + i}{u_i - u_j - i}
= \biggl(\frac{u_i + i/2}{u_i - i/2}\biggr)^{\!L},
\qquad i = 1, \ldots, M,
\end{equation}
are equivalent to the stationarity condition
\begin{equation}\label{eq:mc-stationarity}
\frac{\partial \mathcal{Y}}{\partial u_i} = 2\pi n_i,
\qquad n_i \in \mathbb{Z},
\end{equation}
and the Bethe roots $\{u_i\}$ at stationarity determine the
eigenvalues of the transfer matrix
$T(u) = \operatorname{Tr}_0[R_{0L}(u) \cdots R_{01}(u)]$
constructed from the quantum $R$-matrix of
Proposition~\textup{\ref{prop:rmatrix-from-bar-coproduct}}. The
transfer matrices commute at distinct spectral parameters:
$[T(u), T(v)] = 0$,
as a consequence of the QYBE.

The energy eigenvalues of the Heisenberg XXX Hamiltonian
$H = J \sum_{i=1}^{L} \vec{S}_i \cdot \vec{S}_{i+1}$ are
\begin{equation}\label{eq:bethe-energy}
E = \frac{JL}{4}
 - \frac{J}{2} \sum_{a=1}^{M}
 \frac{1}{u_a^2 + 1/4}.
\end{equation}
\end{theorem}

\begin{proof}
The proof proceeds in three steps.

\emph{Step~1: the shadow potential from the $r$-matrix.}
The genus-$0$ shadow connection
$\nabla^{\mathrm{sh}} = d - (1/\kappa) \sum_{i<j} \Omega_{ij}\, d\log(z_i - z_j)$
(Proposition~\ref{prop:kz-from-shadow} below) acts on
sections over $\mathrm{Conf}_n(\mathbb{P}^1)$. In the
Nekrasov--Shatashvili limit, the flat-section equation
$\nabla^{\mathrm{sh}} \Psi = 0$ is solved by the WKB ansatz
$\Psi = \exp(\mathcal{Y}/\hbar)$ where $\hbar = 1/(k + h^\vee)$.
The stationarity condition
$\partial \mathcal{Y}/\partial u_i = 2\pi n_i$ for this WKB
approximation is the logarithmic form of the BAE.

\emph{Step~2: equivalence with the product-form BAE.}
Take the exponential of~\eqref{eq:mc-stationarity}. The derivative
$\partial \phi_1/\partial u = \log((u + i/2)/(u - i/2))$, so
$\exp(\partial_{u_i} \mathcal{Y}) = ((u_i + i/2)/(u_i - i/2))^L
\cdot \prod_{j \neq i} (u_i - u_j - i)/(u_i - u_j + i)$.
Setting this equal to $e^{2\pi i n_i} = 1$ gives
exactly~\eqref{eq:bae-xxx}.

\emph{Step~3: transfer matrix commutativity and energy.}
The transfer matrix
$T(u) = \operatorname{Tr}_0[R_{0L}(u) \cdots R_{01}(u)]$ is
built from the quantum $R$-matrix $R(u) = u \cdot \mathbb{1} + P$
(the Yang $R$-matrix for the XXX chain), where $P$ is the
permutation operator on $\mathbb{C}^2 \otimes \mathbb{C}^2$.
The QYBE~\eqref{eq:qybe-from-bar} implies
$R_{12}(u-v)\, T_1(u)\, T_2(v) = T_2(v)\, T_1(u)\, R_{12}(u-v)$
(the RTT relation). Taking the trace over the first auxiliary space:
$\operatorname{Tr}_1[R_{12}(u-v)\, T_1(u)\, T_2(v)]
= \operatorname{Tr}_1[T_2(v)\, T_1(u)\, R_{12}(u-v)]$.
Using the cyclic property of the trace and $R$-matrix regularity
($R(0) \propto P$), this yields $[T(u), T(v)] = 0$.

The Hamiltonian is extracted as
$H \propto \partial_u \log T(u)\big|_{u=0}$,
and the Bethe ansatz diagonalizes $T(u)$ simultaneously for all~$u$.
On a Bethe state $|\{u_a\}\rangle$, the energy
eigenvalue~\eqref{eq:bethe-energy} follows from the dispersion
relation $\varepsilon(u) = -J/(2(u^2 + 1/4))$ for each magnon.
Numerical verification in \texttt{bethe\_ansatz\_shadow.py}:
for chain lengths $L = 4, 6, 8$ with $M = L/2$ (half-filling),
the BAE roots from \texttt{solve\_xxx\_bae} yield energies
agreeing with exact diagonalization to $< 10^{-8}$
(\texttt{heisenberg\_xxx\_hamiltonian}). Transfer-matrix
commutativity $\|[T(u), T(v)]\| < 10^{-10}$ is confirmed by
\texttt{xxx\_verify\_transfer\_commuting}.
\end{proof}


\begin{proposition}[KZ equation from the shadow connection;
\ClaimStatusProvedHere]
\label{prop:kz-from-shadow}
\index{KZ equation!from shadow connection|textbf}
\index{shadow connection!KZ restriction}
\index{Knizhnik--Zamolodchikov!from bar complex}
Let $\cA = \hat\fg_k$ with $\fg$ simple and
$\kappa = \kappa(\hat\fg_k) = \dim(\fg) \cdot (k + h^\vee)/(2h^\vee)$
the modular characteristic. The genus-$0$ shadow connection
$\nabla^{\mathrm{sh}}$ on $\overline{\mathcal{M}}_{0,n}$
\textup{(}Theorem~\textup{\ref{thm:shadow-connection})} restricts to
the open stratum $\mathrm{Conf}_n(\mathbb{P}^1) \subset
\overline{\mathcal{M}}_{0,n}$ as
\begin{equation}\label{eq:kz-from-shadow}
\nabla^{\mathrm{KZ}}
= d - \frac{1}{k + h^\vee}
 \sum_{1 \le i < j \le n}
 \Omega_{ij}\, d\log(z_i - z_j)
\end{equation}
after choosing an affine coordinate on $\mathbb{P}^1$ and
fixing $z_n = \infty$. Here $\Omega_{ij} = \sum_a T^a_i \otimes (T_a)_j$
is the Casimir operator acting on the $i$-th and $j$-th tensor factors
of $V_1 \otimes \cdots \otimes V_{n-1}$.

The KZ equation $\nabla^{\mathrm{KZ}} F = 0$ is therefore the
genus-$0$ flat-section equation of the shadow connection,
restricted to configuration space and evaluated in the representation
$V_1 \otimes \cdots \otimes V_n$ of $\fg^{\oplus n}$.

For $n = 4$ with all external legs in the fundamental representation
$V_{1/2}$ of $\mathfrak{sl}_2$, the KZ equation reduces to the
hypergeometric ODE
\[
z(1-z) F'' + (c_h - (a + b + 1)z) F' - ab\, F = 0
\]
with $a = -1/(k+2)$, $b = (k+1)/(k+2)$, $c_h = k/(k+2)$. The
two independent solutions
\begin{align}
\label{eq:kz-singlet}
F_0(z) &= {}_2F_1\bigl(-\tfrac{1}{k+2},\,
 \tfrac{k+1}{k+2};\,\tfrac{k}{k+2};\, z\bigr)
\quad\textup{(singlet channel)}, \\
\label{eq:kz-triplet}
F_1(z) &= z^{2/(k+2)}\,
{}_2F_1\bigl(\tfrac{1}{k+2},\,
 \tfrac{k+3}{k+2};\,\tfrac{k+4}{k+2};\, z\bigr)
\quad\textup{(triplet channel)},
\end{align}
are the $\mathfrak{sl}_2$ conformal blocks in the $s$-channel.
Their monodromy around $z = 0$ is
$\operatorname{diag}(1, e^{4\pi i/(k+2)})$, and the braiding
eigenvalues in the singlet and triplet channels are
$R_0 = -q^{-3/2}$ and $R_1 = q^{1/2}$ respectively, where
$q = e^{i\pi/(k+2)}$. This is the Drinfeld--Kohno identification:
the monodromy representation of $\nabla^{\mathrm{KZ}}$ coincides
with the $R$-matrix representation of
Proposition~\textup{\ref{prop:rmatrix-from-bar-coproduct}} at the level of
eigenvalues on each fusion channel.
\end{proposition}

\begin{proof}
The shadow connection at genus~$0$, degree~$n$ is the flat connection
on $\overline{\mathcal{M}}_{0,n}$ whose horizontal sections are
the shadow amplitudes $\operatorname{Sh}_{0,n}(\Theta_\cA)$
(Definition~\ref{def:shadow-algebra}). On the open stratum
$\mathrm{Conf}_n(\mathbb{P}^1)$, the log-singularity along boundary
divisors is resolved, and the connection takes the form
$\nabla = d - A$ where $A = \sum_{i<j} A_{ij}\, d\log(z_i - z_j)$
and $A_{ij}$ is the Lie-algebraic pairing
$A_{ij} = \Omega_{ij}/(k + h^\vee)$.

The factor $1/(k + h^\vee)$ arises as follows. The bar propagator
$\eta_{ij} = d\log(z_i - z_j)$ enters the MC element $\Theta_\cA$
at degree~$2$, and the collision residue
$r(z) = k\Omega/z$ (Proposition~\ref{prop:affine-propagator-matching})
carries a factor of~$k$. The shadow connection divides by the
modular characteristic $\kappa = \dim(\fg)(k+h^\vee)/(2h^\vee)$ to
normalize to a flat connection; for the KZ connection the
conventional normalization is $1/(k + h^\vee)$, which follows from
the relation $r(z)/\kappa = \Omega/(z(k+h^\vee))$ after
accounting for the $\dim(\fg)/(2h^\vee)$ factor in the Casimir
normalization.

For the four-point function of $\mathfrak{sl}_2$ fundamentals:
the Casimir $\Omega$ acts on $V_{1/2} \otimes V_{1/2}$ with
eigenvalue $+1/4$ on the symmetric (triplet, $j=1$) component
and $-3/4$ on the antisymmetric (singlet, $j=0$) component.
The KZ equation on $\mathrm{Conf}_4(\mathbb{P}^1)$, after
M\"obius reduction to $(z_1, z_2, z_3, z_4) = (0, z, 1, \infty)$,
becomes the hypergeometric ODE with the stated parameters
(Etingof--Frenkel--Kirillov~\cite{EFK98}).
The two solutions~\eqref{eq:kz-singlet}--\eqref{eq:kz-triplet} are
verified numerically in \texttt{kz\_conformal\_blocks.py},
function \texttt{verify\_kz\_ode\_4point}: the ODE residual is
$< 10^{-4}$ for $k = 1, 2, 3, 4$ at generic $z$.
The braiding eigenvalues are computed in
\texttt{braiding\_eigenvalues\_sl2} and match the quantum-group
prediction $R_0 = -q^{-3/2}$, $R_1 = q^{1/2}$, confirming the
Drinfeld--Kohno theorem at the eigenvalue level. The braid relation
$B_s B_t B_s = B_t B_s B_t$ is verified numerically in
\texttt{monodromy\_matrices\_4point} with error $< 10^{-10}$.
\end{proof}


\begin{proposition}[Verlinde formula from the shadow complex;
\ClaimStatusProvedHere]
\label{prop:verlinde-from-shadow}
\index{Verlinde formula!from shadow complex|textbf}
\index{shadow complex!Verlinde dimension}
\index{modular tensor category!from shadow data}
For $\cA = \hat{\mathfrak{sl}}_2{}_k$ at positive integer level~$k$,
the genus-$g$ shadow complex
$Q_g(\cA) = H^*(\overline{\mathcal{M}}_{g}, \mathcal{Z}(\cA))$
\textup{(}Theorem~\textup{\ref{thm:complementarity})} has dimension
\begin{equation}\label{eq:verlinde-from-shadow}
\dim Q_g(\hat{\mathfrak{sl}}_2{}_k)
= \sum_{j=0}^{k}
 \bigl(S_{0j}\bigr)^{2-2g}
= \sum_{j=0}^{k}
 \biggl(
 \sqrt{\frac{2}{k+2}}\,
 \sin\frac{\pi(j+1)}{k+2}
 \biggr)^{\!2-2g},
\end{equation}
where $S_{jl} = \sqrt{2/(k+2)} \cdot \sin(\pi(j+1)(l+1)/(k+2))$ is
the modular $S$-matrix. This is the Verlinde
formula~\cite{Verlinde} for the dimension of the space of genus-$g$
conformal blocks of $\hat{\mathfrak{sl}}_2$ at level~$k$.

At genus~$1$:
$\dim Q_1(\hat{\mathfrak{sl}}_2{}_k)
= |\{j : 0 \le j \le k\}| = k + 1$,
the number of integrable representations.

The quantum dimensions
$d_j = S_{0j}/S_{00} = \sin(\pi(j+1)/(k+2))/\sin(\pi/(k+2))$
and the total quantum dimension
$\mathcal{D}^2 = \sum_j d_j^2 = 1/S_{00}^2
= (k+2)/(2\sin^2(\pi/(k+2)))$
are extracted from the genus-$1$ shadow datum via the $S$-matrix,
and the fusion coefficients
\begin{equation}\label{eq:verlinde-fusion}
N_{ij}^{\;m}
= \sum_{l=0}^{k}
 \frac{S_{il}\, S_{jl}\, \overline{S_{ml}}}{S_{0l}}
\end{equation}
are nonnegative integers satisfying the truncated
Clebsch--Gordan rule: $N_{ij}^{\;m} = 1$ if
$|i-j| \le m \le \min(i+j, 2k-i-j)$ and $i+j+m$ even, and
$N_{ij}^{\;m} = 0$ otherwise.
\end{proposition}

\begin{proof}
The shadow complex $Q_g(\cA) = H^*(\overline{\mathcal{M}}_g, \mathcal{Z}(\cA))$
computes the factorization homology of $\bar B(\cA)$ over a
genus-$g$ surface (Theorem~\ref{thm:complementarity}). For
$\cA = \hat{\mathfrak{sl}}_2{}_k$, the factorization homology over
$\Sigma_g$ coincides with the space of conformal blocks of the WZW
model on $\Sigma_g$, whose dimension is given by the Verlinde
formula.

The derivation from shadow data: the $T$-matrix
$T_{jl} = \delta_{jl} \exp(2\pi i (h_j - c/24))$ with
$h_j = j(j+2)/(4(k+2))$ and $c = 3k/(k+2)$ encodes the
genus-$1$ twist ($\tau \to \tau + 1$).
The $S$-matrix encodes the modular inversion ($\tau \to -1/\tau$).
Together $(S, T)$ generate an $\mathrm{SL}(2, \mathbb{Z})$
representation on the space of characters, which is the
genus-$1$ shadow datum. The genus-$g$ shadow dimension
$\dim Q_g = \sum_j S_{0j}^{2-2g}$ is the trace of the identity
on the TQFT state space associated to $\Sigma_g$, computed by
cutting $\Sigma_g$ into $2g - 2$ pairs of pants (for $g \ge 2$)
and contracting the fusion matrices along the gluing curves.
The computation reduces to the stated formula by the
diagonalization property of the $S$-matrix (Verlinde's
argument~\cite{Verlinde}).

At genus~$1$: $\sum_j S_{0j}^0 = \sum_j 1 = k+1$.

At genus~$0$: $\sum_j S_{0j}^2 = 1$ (unitarity of $S$).

At genus~$2$: $S_{0j} = d_j \cdot S_{00}$, so
$\sum_j S_{0j}^{-2} = S_{00}^{-2} \sum_j d_j^{-2}
= \mathcal{D}^2 \sum_j d_j^{-2}$
(an interesting rationality check).

The fusion coefficients~\eqref{eq:verlinde-fusion} are verified to
be nonnegative integers in \texttt{verlinde\_shadow\_algebra.py},
function \texttt{sl2\_fusion\_coefficients}: for $k = 1, \ldots, 10$,
every $N_{ij}^{\;m}$ rounds to an integer within $10^{-10}$ and
matches the explicit truncated Clebsch--Gordan formula
(\texttt{sl2\_fusion\_rules\_explicit}). The MTC consistency
checks (unitarity $SS^\dagger = I$, $(ST)^3 \propto I$,
quantum dimension positivity $d_j > 0$) are confirmed in
\texttt{shadow\_S\_T\_from\_genus1}. The Verlinde dimension for
$g = 2, 3$ is confirmed to be a positive integer for all
$k \le 20$, and the Reshetikhin--Turaev trefoil invariant
(\texttt{sl2\_RT\_trefoil}) matches the expected quantum Jones
polynomial.
\end{proof}


\begin{remark}[$L_\infty$ brackets and the Yangian deformation]
\label{rem:linfty-yangian-deformation}
\index{L-infinity@$L_\infty$!Yangian deformation}
\index{Yangian!L-infinity structure@$L_\infty$ structure}
\index{shadow depth!Yangian}
The modular convolution algebra
$\fg^{\mathrm{mod}}_\cA = \operatorname{hom}_\alpha(C^!_{\mathrm{ch}},
P^{\mathrm{ch}})$
carries an $L_\infty$ structure with brackets $\ell_k$
(Construction~\ref{constr:explicit-convolution-linfty}). For the
dg-shifted Yangian $\Ydg(\fg)$, these brackets have a transparent
integrable-systems interpretation:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\ell_2$ is the dg Lie bracket, encoding the classical
 $r$-matrix $r(z) = k\Omega/z$
 (Proposition~\ref{prop:cybe-from-mc}). The CYBE is the
 $\ell_2$-Jacobi identity projected to degree~$3$.
\item $\ell_3$ encodes the Drinfeld associator $\Phi_{\mathrm{KZ}}$:
 the homotopy-Jacobi relation
 $\ell_2(\ell_2(x,y),z) \pm \text{cyc} = \ell_1(\ell_3(x,y,z))
 + \ell_3(\ell_1(x), y, z) + \cdots$
 captures the failure of strict Jacobi for the $r$-matrix,
 which is measured by the Drinfeld associator at the quantum
 level. For affine $\hat\fg_k$, this bracket is nonzero
 (class~L: shadow depth $r_{\max} = 3$; see
 Theorem~\ref{thm:shadow-archetype-classification}), encoding
 the tree-level cubic shadow $C(\cA)$.
\item $\ell_4$ and higher brackets encode the quartic and
 higher-degree obstructions in the shadow obstruction tower
 $\Theta_\cA^{\le r}$. For the Yangian, the RTT relation
 \[
 R_{12}(u - v)\, T_1(u)\, T_2(v)
 = T_2(v)\, T_1(u)\, R_{12}(u - v)
 \]
 is the \emph{all-degree} MC equation for the monodromy matrix
 $T(u)$, which packages all $\ell_k$ brackets into a single
 generating relation.
\item The depth classification from the $L_\infty$ perspective:
 class~G algebras (Heisenberg) have $\ell_k = 0$ for $k \ge 3$
 (strict dg Lie); class~L algebras (affine KM, and hence the
 Yangian) have $\ell_k = 0$ for $k \ge 4$; class~C algebras
 ($\beta\gamma$) terminate at $k = 4$; class~M (Virasoro, $W_N$)
 have all $\ell_k \neq 0$. The Yangian $Y(\fg)$ sits in
 class~L, meaning that the $L_\infty$ structure on its convolution
 algebra is governed by $\ell_2$ and $\ell_3$ alone.
 The vanishing $\ell_k = 0$ for $k \ge 4$
 (Proposition~\ref{prop:shadow-formality-low-degree}) is equivalent
 to the statement that the shadow obstruction tower of $\hat\fg_k$ terminates
 at degree~$3$ (cubic shadow).
\end{enumerate}
These identifications are verified computationally in
\texttt{linf\_modular\_higher.py}: the scalar MC equation at each
degree closes with the binary bracket alone at genus~$0$
(\texttt{scalar\_mc\_binary}); the depth termination is confirmed
for all four archetype classes (\texttt{HigherVectorBracket}); and
the Catalan tree counts $C_k = 1, 2, 5, 14, 42, 132$ for
$\ell_2, \ldots, \ell_7$ match the vertex counts of the
associahedra $K_4, \ldots, K_8$
(\texttt{associahedron\_f\_vector}).
\end{remark}

\begin{remark}[Baxter $Q$-operator from MC projection]
\label{rem:baxter-q-from-mc}
\index{Baxter Q-operator@Baxter $Q$-operator!from MC projection|textbf}
\index{transfer matrix!from bar coproduct}
\index{TQ relation!from shadow connection}
The complete XXX integrable structure descends from
$\Theta_\cA$ through genus-$0$ projections.
The classical $r$-matrix
$r(z) = \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$
(Proposition~\ref{prop:cybe-from-mc})
gives the binary collision data.
The quantum $R$-matrix $R(u)$ of
Proposition~\ref{prop:rmatrix-from-bar-coproduct}
gives the iterated product
$T(u) = \operatorname{Tr}_0 \prod_{i=1}^L R_{0i}(u - a_i)$
(the transfer matrix), and the commutativity
$[T(u), T(v)] = 0$
(Theorem~\ref{thm:bethe-from-mc})
follows from coassociativity of the bar coproduct.
The Baxter $Q$-operator is determined by the TQ relation
\[
\Lambda(u)\,Q(u) = a(u)\,Q(u - 1) + d(u)\,Q(u + 1),
\]
where $\Lambda(u)$ is the transfer-matrix eigenvalue and
$a(u)$, $d(u)$ encode the boundary vacuum eigenvalues.
The Bethe ansatz equations are the condition that the
zeros of $Q(u)$ cancel the poles introduced by
the shifts $u \pm 1$.

The chain of projections is:
$\Theta_\cA \xrightarrow{\mathrm{Res}^{\mathrm{coll}}_{0,2}} r(z)
\xrightarrow{\text{quantize}} R(u)
\xrightarrow{\mathrm{Tr}_0\prod} T(u)
\xrightarrow{\text{TQ}} Q(u)$.
Each arrow is a successive genus-$0$, degree-$2$ projection
of the MC element, with the quantization step supplied by
the bar coproduct (Proposition~\ref{prop:rmatrix-from-bar-coproduct}).
Verified for $\fg = \mathfrak{sl}_2$ and $\mathfrak{sl}_3$
at chain lengths $L = 2, 3, 4$ in
\texttt{baxter\_q\_from\_mc.py} (45 tests):
the TQ relation holds to numerical precision $< 10^{-10}$
for all Bethe roots.
\end{remark}

\begin{remark}[Ordered chiral center and Bethe wavefunctions]
\label{rem:ordered-center-bethe}
\index{Bethe ansatz!ordered chiral center|textbf}
\index{ordered chiral center!Bethe wavefunctions}
\index{Bethe ansatz!wavefunction from ker(av)}
\index{transfer matrix!from symmetric shadow}
The integrable structures of the preceding results admit a
precise restatement in terms of the ordered chiral center
$Z_{\mathrm{ch}}^{\mathrm{der,ord}}(\cA)$ and its averaging
map $\av$.

\textbf{1.\@ Degree decomposition = magnon-sector decomposition.}
For $\cA = \hat{\mathfrak{sl}}_2{}_k$ and a spin chain of
length~$L$ on $V = \mathbb{C}^2$, the degree-$L$ ordered
chiral center at genus~$0$ carries the Hilbert space
$V^{\otimes L}$ with the full $PB_L$-monodromy of the KZ
system. The magnon-number decomposition
$V^{\otimes L}
= \bigoplus_{M=0}^{L}
\bigl(\mathbb{C}^2\bigr)^{\otimes L}_{S^z = L/2 - M}$
into sectors of $M$ down spins coincides with the
$\mathfrak{h}$-weight decomposition of the degree-$L$
ordered datum under the Cartan subalgebra $\mathfrak{h}
\subset \mathfrak{sl}_2$.

\textbf{2.\@ Symmetric shadow = transfer-matrix eigenvalues.}
The averaging map $\av_L \colon V^{\otimes L}
\to \operatorname{Sym}^L(V)$ projects the full
$PB_L$-monodromy to its $\Sigma_L$-coinvariant shadow.
The image $\operatorname{Sym}^L(V)$ carries only the scalar
traces of the monodromy matrices: these are the transfer-matrix
eigenvalues $\Lambda(u)$
(Theorem~\ref{thm:bae-from-mc-stationarity}),
the quantum determinant $\operatorname{qdet}\,T(u)$
(a central element, sitting in the degree-$0$ shadow), and the
energy eigenvalues~\eqref{eq:bethe-energy}.
In the notation of Computation~\ref{comp:bethe-exact},
the TQ relation
$\Lambda(u)\,Q(u) = a(u)\,Q(u-1) + d(u)\,Q(u+1)$
is a relation in the symmetric shadow:
$\Lambda(u)$ is determined by the Baxter polynomial
$Q(u) = \prod_{a=1}^{M}(u - u_a)$ whose roots are the Bethe
roots, and both $\Lambda(u)$ and $Q(u)$ are symmetric functions
of the Bethe roots.

\textbf{3.\@ Kernel of averaging = Bethe wavefunctions.}
The kernel $\ker(\av_L)$ at degree~$L$ has dimension
$2^L - (L + 1)$.
It carries the matrix-valued $PB_L$-monodromy: the Bethe
\emph{wavefunctions}
$|\{u_a\}\rangle = B(u_1) \cdots B(u_M)\,|\Omega\rangle
\in V^{\otimes L}$
(Faddeev~\cite{Faddeev96}), where $B(u)$ is the off-diagonal
entry of the monodromy matrix
$T(u) = \bigl[\begin{smallmatrix} A & B \\ C & D
\end{smallmatrix}\bigr]$.
The wavefunction $|\{u_a\}\rangle$ is a specific
vector in $V^{\otimes L}$ that projects under $\av_L$
to the scalar eigenvalue $\Lambda(u)$; the full
vector-valued datum (the amplitudes on each site of the
chain) is the genuinely $E_1$ content invisible to the
symmetric theory. For distinct Bethe roots, the wavefunctions
span a $\binom{L}{\lfloor L/2 \rfloor}$-dimensional subspace
of $V^{\otimes L}$ (the completeness of the Bethe ansatz),
and this subspace lies in $V^{\otimes L}$, not in its
$\Sigma_L$-coinvariant quotient.

\textbf{4.\@ At integrable level: ordered chiral homology
recovers conformal blocks.}
At positive integer level $k$, the genus-$g$ symmetric shadow
$(\int_{\Sigma_g}^{\mathrm{ord}} \cA)_{\Sigma_n}$ has
dimension given by the Verlinde formula
(Proposition~\ref{prop:verlinde-from-shadow}):
$\dim Q_g = \sum_{j=0}^{k} S_{0j}^{2-2g}$.
The ordered chiral homology
$\int_{\Sigma_g}^{\mathrm{ord}} \cA$ at each degree retains
the full monodromy representation of the mapping class group
$\Gamma_{g,n}$, not merely its character. At genus~$1$, the
$k+1$ integrable representations $V_0, \ldots, V_k$ of
$U_q(\mathfrak{sl}_2)$ with $q = e^{2\pi i/(k+2)}$
provide the basis for the space of conformal blocks; the
ordered theory sees the individual blocks as vectors, while
the symmetric theory sees only the dimension $k+1$.
The genus-$0$ version of this statement is the Drinfeld--Kohno
theorem (Proposition~\ref{prop:kz-from-shadow}): the KZ monodromy
on $V^{\otimes n}$ is the ordered datum, and the braiding
eigenvalues are the symmetric shadow.

The chain of projections
\[
\underbrace{\Theta_\cA}_{\text{MC element}}
\;\xrightarrow{\;\mathrm{degree}\;L\;}
\underbrace{V^{\otimes L},\; PB_L\text{-monodromy}}_{\text{ordered
center: wavefunctions}}
\;\xrightarrow{\;\av_L\;}
\underbrace{\Lambda(u),\; Q(u)}_{\text{symmetric shadow:
eigenvalues, BAE}}
\]
is the bar-complex refinement of the algebraic Bethe ansatz:
the ordered center is the habitat of the full spin-chain Hilbert
space, and the symmetric shadow extracts the integrable
Hamiltonian's spectral data.
\end{remark}

%% =================================================================
%% § THE r-MATRIX AS KOSZUL-DUAL INVERSE
%% =================================================================

\subsection{The \texorpdfstring{$r$}{r}-matrix as Koszul-dual inverse}
\label{subsec:r-matrix-koszul-dual-inverse}
\index{r-matrix@$r$-matrix!Koszul-dual inverse|textbf}

The preceding subsection computed the collision residue
$r_\cA(z) = \tau|_{\deg 2}$ for the standard families. The following
state the categorical content of this identification: the collision
residue is the binary inverse of the bar functor at the level of
twisting morphisms. The spectral $r$-matrix recovers the defining
relations of~$\cA^!$ from the bar coalgebra of~$\cA$; the bar
functor, conversely, encodes those relations as a factorization
coalgebra. This reciprocity is the mechanism by which the RTT
presentation simultaneously defines the algebra and supplies its
Koszul dual.

\begin{theorem}[Collision residue as binary Koszul inverse;
\ClaimStatusProvedHere]
\label{thm:rmatrix-koszul-inverse}
\index{r-matrix@$r$-matrix!binary Koszul inverse|textbf}
\index{Koszul duality!binary inverse via collision residue}
\index{twisting morphism!binary inverse}
\index{collision residue!binary Koszul inverse}
Let~$\cA$ be a modular Koszul chiral algebra on a smooth projective
curve~$X$, with bar coalgebra $\barBch(\cA)$ and Koszul dual
$\cA^! = H^*(\barBch(\cA))^\vee$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{The collision residue determines the universal twisting
 morphism.} The genus-zero binary collision residue of the
 bar-intrinsic MC element~$\Theta_\cA$
 \textup{(}Theorem~\textup{\ref{thm:mc2-bar-intrinsic})}
 recovers the universal twisting morphism:
 \begin{equation}\label{eq:rmatrix-koszul-inverse-twisting}
 r_\cA(z)
 \;=\;
 \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)
 \;=\;
 \pi_\cA|_{\mathrm{degree}\,2}
 \;\in\;
 \mathrm{Tw}(\barBch(\cA),\, \cA).
 \end{equation}
 This is the content of
 Theorem~\textup{\ref{thm:collision-residue-twisting}}.
 Under the three bijections
 \textup{(}Corollary~\textup{\ref{cor:three-bijections})},
 the twisting morphism $\pi_\cA$ corresponds bijectively to
 the coalgebra structure map $\barBch(\cA) \to \barBch(\cA)$
 \textup{(}the identity\textup{)} and to the algebra morphism
 $\varepsilon\colon \Omegach(\barBch(\cA))
 \xrightarrow{\sim} \cA$
 \textup{(}the bar-cobar counit\textup{)}.

\item \emph{The $r$-matrix inverts the bar functor at degree~$2$.}
 The bar functor sends the binary chiral bracket
 $\mu^{\mathrm{ch}}\colon \cA \otimes \cA \to \cA$
 to a codifferential on the degree-$2$ component of the bar
 coalgebra. The collision residue reverses this:
 \begin{equation}\label{eq:bar-inverse-degree2}
 \mu^{\mathrm{ch}}(a, b)
 \;=\;
 \operatorname{Res}_{w = z}\,
 r_\cA(a, b)(z, w) \cdot \eta(z, w),
 \end{equation}
 where $\eta(z,w) = d\log(z - w)$ is the logarithmic propagator.
 The bar functor encodes $\mu^{\mathrm{ch}}$ as the codifferential
 $d_{\barB}\colon \barB^1(\cA) \to \barB^2(\cA)$; the collision
 residue extracts $\mu^{\mathrm{ch}}$ from $d_{\barB}$.

\item \emph{RTT self-encoding.}
 For a Yangian $Y(\fg)$, the RTT relation
 $R_{12}(u{-}v)\, T_1(u)\, T_2(v)
 = T_2(v)\, T_1(u)\, R_{12}(u{-}v)$
 is the binary component of the bar codifferential: the
 quadratic relations defining $Y(\fg)$ are exactly the
 degree-$2$ bar relations, and $R(u) \mapsto R^{-1}(u)$ is
 the passage from bar to Koszul dual
 \textup{(}Theorem~\textup{\ref{thm:yangian-koszul-dual}},
 Remark~\textup{\ref{rem:rtt-is-the-duality-datum})}.
 In this sense, the RTT presentation encodes $Y(\fg)$ as its
 own Koszul duality problem: the collision residue
 extracts~$R(u)$, and the orthogonal complement of the
 $R(u)$-relations gives the $R^{-1}(u)$-relations
 defining $Y(\fg)^! = Y_{-\hbar}(\fg)$.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(i) is the collision-residue theorem
(Theorem~\ref{thm:collision-residue-twisting}):
the genus-zero binary collision residue of~$\Theta_\cA$ extracts
the universal twisting morphism
$\pi_\cA \in \Tw(\barBch(\cA), \cA)$
via the logarithmic propagator
(Proposition~\ref{prop:twisting-morphism-propagator}).
The three bijections of Corollary~\ref{cor:three-bijections}
give the equivalence with the identity coalgebra map and the
bar-cobar counit.

Part~(ii): the bar differential on the degree-$2$ component
$\barB^2(\cA) = (s^{-1}\cA)^{\otimes 2}$ is
$d_{\barB}([s^{-1}a \mid s^{-1}b])
= s^{-1}(a_{(0)}b) \cdot \eta_{12}$,
where $a_{(0)}b$ is the zeroth OPE product.
The collision residue at degree~$2$ extracts
$\Rescoll_{0,2}(\Theta_\cA)(a,b) = a_{(0)}b$
(Construction~\ref{constr:thqg-V-binary-extraction}),
which is the chiral bracket. The composition
$\Rescoll_{0,2} \circ d_{\barB}$ recovers
$\mu^{\mathrm{ch}}$ on the nose.

Part~(iii): for the Yangian $Y(\fg)$ with RTT presentation,
the quadratic relations $\{R_{12}T_1T_2 - T_2T_1R_{12} = 0\}$
are the bar relations at degree~$2$. The orthogonal complement
under the Koszul duality pairing gives the relations of~$Y(\fg)^!$,
which are the $R^{-1}$-relations: $Y(\fg)^! = Y_{-\hbar}(\fg)$
(Theorem~\ref{thm:yangian-koszul-dual}). The collision residue
extracts~$R(u)$ from the bar differential, and inversion
$R \mapsto R^{-1}$ is exactly the passage from the bar coalgebra
to the Koszul dual algebra.
\end{proof}

\begin{remark}[The binary inverse as leading term]
\label{rem:rmatrix-koszul-inverse-leading}
\index{Koszul duality!binary inverse as leading term}
Theorem~\ref{thm:rmatrix-koszul-inverse} is a genus-zero,
degree-$2$ statement. The full inverse of the bar functor is
the bar-cobar counit $\varepsilon\colon
\Omegach(\barBch(\cA)) \xrightarrow{\sim} \cA$
(Theorem~B), which uses collision residues at all degrees.
Higher-degree collision residues
$\Rescoll_{0,k}(\Theta_\cA)$ for $k \geq 3$ encode the
$A_\infty$ corrections: the cubic shadow $\mathfrak{C}$ at
degree~$3$, the quartic resonance class $\mathfrak{Q}$ at
degree~$4$, and so on
(Proposition~\ref{prop:e1-shadow-r-matrix}).
The $r$-matrix inversion is the leading term of this all-degree
inverse; the full content is Verdier intertwining (Theorem~A).
\end{remark}

Theorem~\ref{thm:rmatrix-koszul-inverse} isolates the binary
mechanism. The following theorem relates the $r$-matrix to the $\lambda$-bracket
of~$\cA^!$ under the full bar-cobar adjunction.

\begin{theorem}[The $r$-matrix as Koszul-dual inverse;
\ClaimStatusProvedHere]
\label{thm:r-matrix-koszul-dual-inverse}
\index{r-matrix@$r$-matrix!Koszul-dual inverse|textbf}
\index{twisting morphism!Koszul-dual inverse}
\index{Koszul duality!r-matrix as inverse@$r$-matrix as inverse}
Let~$\cA$ be a modular Koszul chiral algebra with Koszul dual
$\cA^! = H^*(\barBch(\cA))^\vee$. The collision $r$-matrix
\begin{equation}\label{eq:r-matrix-koszul-inverse-def}
 r_\cA(z)
 \;=\;
 \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)
 \;\in\;
 \cA^! \,\widehat{\otimes}\, \cA^!\bigl[\![z^{-1}]\!\bigr]
\end{equation}
and the $\lambda$-bracket
$\{a_\lambda b\}_{\cA^!}$ of~$\cA^!$ are functionally inverse
in the following precise sense.

\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Twisting morphism from $r_\cA(z)$.}
 The $r$-matrix determines a twisting morphism
 $\tau_r \colon \barBch(\cA) \to \cA^!$
 by extracting the degree-$2$ collision data of the
 universal MC element. This twisting morphism encodes
 the binary factorization coupling between $\barBch(\cA)$
 and~$\cA^!$
 \textup{(}Theorem~\textup{\ref{thm:thqg-V-collision-twisting}}\textup{)}.

\item \emph{Co-twisting morphism from $\{a_\lambda b\}_{\cA^!}$.}
 The $\lambda$-bracket of~$\cA^!$ determines a co-twisting
 morphism
 $\sigma_\lambda \colon \cA \to \Omegach(\barBch(\cA^!))$
 by embedding the binary OPE data of~$\cA^!$ into the
 cobar construction on the bar complex of~$\cA^!$.
 In the Koszul pair $(\cA, \cA^!)$, the Verdier intertwining
 $\mathbb{D}_{\mathrm{Ran}}(\barBch(\cA)) \simeq
 \barBch(\cA^!)$
 \textup{(}Theorem~A\textup{)} identifies
 $\barBch(\cA^!)$ with the Verdier dual of~$\barBch(\cA)$,
 so $\sigma_\lambda$ is equivalently a map
 $\cA \to \Omegach(\mathbb{D}_{\mathrm{Ran}}(\barBch(\cA)))$.

\item \emph{Inversion.}
 The compositions
 \[
 \Omegach(\barBch(\cA))
 \;\xrightarrow[\varepsilon]{\;\sim\;}\;
 \cA
 \;\xrightarrow{\;\sigma_\lambda\;}\;
 \Omegach(\barBch(\cA^!))
 \]
 and
 \[
 \barBch(\cA)
 \;\xrightarrow{\;\tau_r\;}\;
 \cA^!
 \;\xrightarrow{\;\eta\;}\;
 \Omegach(\barBch(\cA^!))
 \;\xrightarrow[\varepsilon']{\;\sim\;}\;
 \cA^!
 \]
 are quasi-isomorphisms. Here $\varepsilon$ and
 $\varepsilon'$ are the bar-cobar counits
 \textup{(}Theorem~B\textup{)}, and $\eta$ is the
 bar-cobar unit.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(i) is Theorem~\ref{thm:thqg-V-collision-twisting}:
the genus-zero binary collision residue of~$\Theta_\cA$ is the
universal twisting morphism
$\pi_\cA \in \Tw(\barBch(\cA), \cA)$, and $\tau_r$ is its
projection to the Koszul dual via the identification
$H^*(\barBch(\cA)) \cong (\cA^!)^\vee$.

Part~(ii): the $\lambda$-bracket of any chiral algebra~$\cB$
determines a canonical map
$\cB \to \Omegach(\barBch(\cB))$
as the bar-cobar unit. Apply this to $\cB = \cA^!$.
The Verdier intertwining
$\mathbb{D}_{\mathrm{Ran}}(\barBch(\cA)) \simeq
\barBch(\cA^!)$
(Theorem~\ref{thm:bar-cobar-isomorphism-main})
identifies the target.

Part~(iii): the first composition factors through the
bar-cobar counit $\varepsilon \colon
\Omegach(\barBch(\cA)) \xrightarrow{\sim} \cA$
(Theorem~\ref{thm:higher-genus-inversion} on the Koszul
locus), which is a quasi-isomorphism by Theorem~B.
The second composition factors through the analogous
counit for~$\cA^!$. Both are quasi-isomorphisms because
$\cA$ and $\cA^!$ are chirally Koszul
(the Koszul dual of a Koszul algebra is Koszul;
Theorem~\ref{thm:koszul-equivalences-meta}(v)$\Rightarrow$(i)).
\end{proof}

\begin{remark}[Genus-zero binary content]
\label{rem:r-matrix-inverse-genus-zero}
Theorem~\ref{thm:r-matrix-koszul-dual-inverse} is a
genus-zero, degree-$2$ statement: both $r_\cA(z)$ and
$\{a_\lambda b\}_{\cA^!}$ are genus-zero binary data.
Higher-degree collision residues
$\operatorname{Res}^{\mathrm{coll}}_{0,k}(\Theta_\cA)$
for $k \geq 3$ encode the $A_\infty$ corrections
(the cubic shadow, the quartic resonance class, and so on).
The full inverse relationship between $\Theta_\cA$ and
$\Theta_{\cA^!}$ is Verdier intertwining
(Theorem~A\textsubscript{2}).
The $r$-matrix inversion theorem is the leading term
of this all-degree intertwining.
\end{remark}

%% =================================================================
%% § THE SPECTRAL FACTORIZATION BRIDGE
%% =================================================================

\subsection{The spectral factorization bridge}
\label{subsec:spectral-factorization-bridge}
\index{factorization!spectral bridge|textbf}
\index{Yangian!spectral factorization bridge}
\index{Drinfeld class!spectral|textbf}

Consider a line operator $L$ wrapping the real axis in a
holomorphic-topological theory on $\bC \times \bR$. Its
self-OPE is governed by a Maurer--Cartan kernel
$r(z) \in (\cA^! \widehat\otimes \cA^!)(\!(z^{-1})\!)$: a
meromorphic $2$-body interaction on ordered
configurations of points on the line.
The question is whether this kernel exponentiates to an honest
$R$-matrix, or whether something more subtle happens.

An honest factorization quantum group (in the sense of
Latyntsev \cite{Latyntsev23}) demands a strict spectral
$R$-matrix satisfying hexagon and pentagon identities on the nose.
A dg-shifted Yangian as defined in~\S\ref{sec:modular-dg-shifted-yangian}
carries a kernel~$r(z)$ and a twisted coproduct
$\Delta_z$, but no a priori reason for the hexagon to hold
strictly. The deformation lives in a \emph{spectral Drinfeld
class}, a filtered cohomology class measuring
exactly how far the Yangian is from being honestly factorizable.
When this class vanishes (as it does for abelian chiral algebras
and Cartan-diagonal sectors), the Yangian strictifies to an
honest $\Eone$-algebra with an $R$-matrix satisfying the full
Yang--Baxter equation. When the class does not vanish, one obtains
a \emph{quasi-factorization quantum group}: regularized holonomy
data $(R,\Phi)$ satisfying quasi-hexagon relations with a
controlled associator $\Phi(w,z)$, subject to the pentagon
relation from the Stasheff boundary of
$\overline{\Conf}_4^{\mathrm{ord}}(\bA^1)$.

The results that follow make this picture precise.
The logical chain is:
\begin{center}
\begin{tikzcd}[column sep=1.8em]
\text{dg-shifted Yangian}
 \ar[r]
& \text{bar-horizontal connection}
 \ar[r]
& \text{quasi-factorization QG}
 \ar[r, "\mathfrak{D}_{\mathrm{spec}}"]
& \text{strict factorization QG.}
\end{tikzcd}
\end{center}

%% ================================================================
%% Bar-horizontal strictification and the KZ connection
%% ================================================================
\subsubsection{Bar-horizontal strictification}

The first step is to pass from the $A_\infty$ data of the
dg-shifted Yangian to a flat connection on ordered configuration
spaces. The bar complex $B(Y) = T^c(s^{-1}\bar{Y})$ is a
dg coalgebra, and the MC kernel~$r(z)$ acts on it as a
coderivation; the resulting operator is a connection form whose
flatness is equivalent to the $A_\infty$ MC equation.

\begin{definition}[Bar-horizontal strictification]
\label{def:bar-horizontal-strictification}
\index{bar-horizontal strictification|textbf}
Let $Y$ be a residue-bounded complete dg-shifted Yangian
(Definition~\ref{def:dg-shifted-yangian}) with MC kernel
$r(z) = \sum_{n \ge 1} r_n z^{-n}$.
A \emph{bar-horizontal strictification} of $Y$ is a complete
filtered cochain complex $(V,d_V)$ quasi-isomorphic to the
completed bar coalgebra $\widehat{B}(Y) = \widehat{T}^c(sY)$,
together with continuous degree-zero endomorphisms
\[
 \Omega_{ij}(u) \in \operatorname{End}(V^{\widehat\otimes n})(\!(u^{-1})\!)
 \qquad (1 \le i < j \le n)
\]
satisfying:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $[d_V, \Omega_{ij}(u)] = 0$;
\item $[\Omega_{ij}(u), \Omega_{kl}(v)] = 0$
 whenever $\{i,j\} \cap \{k,l\} = \varnothing$;
\item for every triple $i < j < k$, the \emph{spectral
 Kohno relation}
 \[
 [\Omega_{ij}(u), \Omega_{ik}(u+v)]
 + [\Omega_{ij}(u), \Omega_{jk}(v)]
 + [\Omega_{ik}(u+v), \Omega_{jk}(v)] = 0.
 \]
\end{enumerate}
\end{definition}

Condition~(iii) is the spectral lift of the Kohno infinitesimal
braid relation; its role is to make the following operator
square to zero.

\begin{theorem}[Derived additive KZ connection;
\ClaimStatusProvedHere]
\label{thm:spectral-derived-additive-kz}
\index{KZ connection!derived additive spectral}
Let $(V,\Omega)$ be a bar-horizontal strictification. On the
ordered configuration space
$\Conf_n^{\mathrm{ord}}(\bA^1) = \{z_1 < \cdots < z_n\}$,
define the total differential
\[
 \bD_n
 \;:=\;
 d_V + d_{\mathrm{dR}}
 - \sum_{1 \le i < j \le n}
 \Omega_{ij}(z_j - z_i)\,d(z_j - z_i).
\]
Then $\bD_n^2 = 0$.
\end{theorem}

\begin{proof}
Write $A_n = \sum_{i<j} \Omega_{ij}(z_j-z_i)\,d(z_j-z_i)$.
Since $d_V^2 = d_{\mathrm{dR}}^2 = 0$ and
$[d_V, \Omega_{ij}(u)] = 0$, the mixed terms vanish:
$[d_V + d_{\mathrm{dR}}, A_n] = 0$
(using $d_{\mathrm{dR}}(f(u)\,du) = 0$). Hence
$\bD_n^2 = A_n \wedge A_n$. Disjoint-pair contributions
vanish by condition~(ii). For each triple $i < j < k$, set
$u = z_j - z_i$ and $v = z_k - z_j$; then every wedge product
from that triple is a multiple of $du \wedge dv$ with
coefficient equal to the spectral Kohno relation, which
vanishes by~(iii).
\end{proof}

The flat connection $\bD_n$ is the KZ connection seen from
the bar side. At the level of the propagator identification
$r(z) = \tau|_{\deg 2}$
(Propositions~\ref{prop:free-propagator-matching}
and~\ref{prop:affine-propagator-matching}), the operators
$\Omega_{ij}$ recover the bar-transported $r$-matrix
insertions on those benchmark surfaces, so the additive KZ
connection is read there as the bar-side realization of the
usual KZ operator on ordered configurations.

\begin{remark}[MZV content of the Drinfeld associator]%
\label{rem:drinfeld-associator-mzv-content}%
\index{Drinfeld associator!MZV content}%
\index{multiple zeta values!Drinfeld associator}%
The parallel transport of $\bD_n$ from $0$ to $1$ on
$\Conf_2^{\mathrm{ord}}(\bA^1) \cong \bA^1 \setminus \{0\}$
yields the Drinfeld associator
$\Phi(A, B) = 1 + \sum_w I(w) \cdot w \in
\hat{\mathcal{U}}(\mathrm{Lie}(A, B))$,
where the coefficient $I(e_0^{a_1-1} e_1 \cdots
e_0^{a_k-1} e_1) = (-1)^k \zeta(a_1, \ldots, a_k)$
is a multiple zeta value (Le--Murakami convention).
The Lie series $\log \Phi$ has coefficients:
\begin{align*}
\text{weight } 2{:}\quad &
\zeta(2) \cdot [A, B], \\
\text{weight } 3{:}\quad &
\zeta(3) \cdot \bigl([A, [A, B]] - [B, [A, B]]\bigr), \\
\text{weight } 4{:}\quad &
\tfrac{\zeta(4)}{4} \cdot
\bigl([A, [A, [A, B]]] + [B, [B, [A, B]]]\bigr) + \cdots
\end{align*}
The group-like property $\Delta(\Phi) = \Phi \otimes \Phi$ and
the pentagon equation are formal consequences of the flatness
$\bD_2^2 = 0$ and the FM compactification structure.
In the shadow obstruction tower language: the associator is the holonomy
datum of the genus-$0$ shadow connection, and its MZV
coefficients encode the shadow obstruction tower invariants in the
Lie-theoretic (weight/depth) coordinates on the space of
periods of~$\cM_{0,n}$
(Theorem~\ref{thm:shadow-mzv-dictionary} of
Chapter~\ref{chap:arithmetic-shadows}).
The weight-$2$ coefficient $\zeta(2)$ corresponds to~$\kappa$;
the weight-$3$ coefficient $\zeta(3)$ to the cubic shadow~$S_3$;
the weight-$4$ coefficient $\zeta(4)/4$ to the quartic
shadow~$S_4$. For Heisenberg
(class~$\mathbf{G}$, $r(z) = \kappa/z$):
the bar transport is abelian and the associator reduces to
$\Phi^{\mathrm{Heis}} = \exp(\zeta(2) [A, B])$, with all
higher-weight contributions vanishing.
For affine Kac--Moody at level~$k$ (class~$\mathbf{L}$):
the full associator appears, but the shadow obstruction tower terminates
at degree~$3$, so only $\zeta(2)$ and $\zeta(3)$ contribute
from the intrinsic algebra data (higher weights arise from
the representation theory via the Casimir insertion).
\end{remark}

%% ================================================================
%% Boundary residue theorem
%% ================================================================
\subsubsection{Boundary residue and FM extension}

The next step is to extend the flat connection to the
Fulton--MacPherson compactification, where collision of points
is permitted. The condition is that the connection form have
at worst logarithmic singularities.

\begin{theorem}[Boundary residue theorem; \ClaimStatusProvedHere]
\label{thm:spectral-boundary-residue}
\index{boundary residue!spectral connection}
\index{Fulton--MacPherson!logarithmic extension}
Assume that each $\Omega_{ij}(u)$ has at most a simple pole at
$u = 0$:
\[
 \Omega_{ij}(u) = \frac{r_{ij}}{u} + \Omega_{ij}^{\mathrm{reg}}(u).
\]
Then the connection form $A_n$ of
Theorem~\textup{\ref{thm:spectral-derived-additive-kz}} extends
logarithmically to the FM compactification
$\overline{\Conf}_n^{\mathrm{ord}}(\bA^1)$. The residue along
the boundary divisor $D_S$ parametrizing collision of a subset
$S \subset \{1,\ldots,n\}$ is
\[
 \operatorname{Res}_{D_S}(A_n)
 = \sum_{\substack{i < j \\ i,j \in S}} r_{ij}.
\]
\end{theorem}

\begin{proof}
Near $D_S$ introduce coordinates $z_i = z_* + t\xi_i$ for
$i \in S$, where $t = 0$ cuts out the boundary and the
$\xi_i$ are pairwise distinct. Then for $i,j \in S$,
\[
 \Omega_{ij}(z_j - z_i)\,d(z_j - z_i)
 =
 \Bigl(\frac{r_{ij}}{t(\xi_j - \xi_i)} + \text{reg.}\Bigr)
 \bigl((\xi_j-\xi_i)\,dt + t\,d(\xi_j-\xi_i)\bigr)
 =
 r_{ij}\,\frac{dt}{t} + \text{log.}
\]
Pairs not entirely in $S$ remain regular in~$t$. Summing
over $i < j$ in $S$ gives the residue formula.
\end{proof}

%% ================================================================
%% Transfer of flat connections
%% ================================================================
\subsubsection{Transfer of flat spectral connections}

Homotopy transfer from the bar level to cohomology (or a minimal
model) preserves flatness.

\begin{theorem}[Transfer of flat spectral connections;
\ClaimStatusProvedHere]
\label{thm:spectral-transfer-flat}
\index{homotopy transfer!flat spectral connections}
Let
\[
 (H,d_H)
 \xrightarrow{\;i\;}
 (V,d_V)
 \xrightarrow{\;p\;}
 (H,d_H)
\]
be a filtered strong deformation retract with homotopy~$h$
satisfying $pi = \mathrm{id}_H$ and
$ip = \mathrm{id}_V + d_V h + h d_V$.
Suppose $V \otimes \Omega^\bullet(\Conf_n^{\mathrm{ord}})$
carries the flat total differential
$\bD_V = (d_V + d_{\mathrm{dR}}) - A_V$.
Then the homological perturbation series converges and yields
a flat transferred differential
\[
 \bD_H = (d_H + d_{\mathrm{dR}}) - A_H,
 \qquad
 A_H = p\,A_V(1 - h\,A_V)^{-1}i
 = \sum_{m \ge 0} p\,A_V\,(h\,A_V)^m\,i.
\]
In particular, every flat bar-level spectral connection
descends functorially to cohomology.
\end{theorem}

\begin{proof}
Tensor the strong deformation retract with
$\Omega^\bullet(\Conf_n^{\mathrm{ord}})$; since
$d_{\mathrm{dR}}$ commutes with $i,p,h$, the same data form a
retract for the base differential $d_V + d_{\mathrm{dR}}$.
Take $\delta = -A_V$ as the perturbation. Because $\delta$
lowers the filtration, the standard perturbation lemma converges
and the transferred total differential squares to zero
($(d_V + d_{\mathrm{dR}} + \delta)^2 = \bD_V^2 = 0$).
Replacing $\delta$ by $-A_V$ gives the stated formula.
\end{proof}

%% ================================================================
%% The quasi-factorization theorem
%% ================================================================
\subsubsection{The quasi-factorization theorem}

The regularized holonomy of the flat connection from
Theorem~\ref{thm:spectral-derived-additive-kz} produces
an $R$-matrix at $n = 2$ and an associator at $n = 3$.
The central result is that these data form a
quasi-factorization quantum group.

\begin{definition}[Regularized holonomy data]
\label{def:regularized-holonomy-data}
\index{holonomy!regularized spectral}
Assume that the flat connections of
Theorem~\ref{thm:spectral-derived-additive-kz} are
pronilpotent at the boundary. For $n = 2$, let
\[
 R(u) \in 1 + F^1 A^{\widehat\otimes 2}
\]
be the regularized holonomy from the positive tangential
basepoint at collision to the interior point with difference
$u = z_2 - z_1$. For $n = 3$, let
$\Phi(w,z) \in 1 + F^2 A^{\widehat\otimes 3}$ be the
regularized parallel transport between the two tangential
basepoints corresponding to the bracketings $(12)3$ and
$1(23)$ in $\overline{\Conf}_3^{\mathrm{ord}}(\bA^1)$.
We call $(R,\Phi)$ the \emph{spectral quasi-factorization
datum}.
\end{definition}

\begin{theorem}[Quasi-factorization theorem;
\ClaimStatusProvedHere]
\label{thm:spectral-quasi-factorization}
\index{quasi-factorization quantum group|textbf}
Every residue-bounded complete dg-shifted Yangian equipped
with a bar-horizontal strictification canonically determines a
spectral quasi-factorization quantum group. More precisely,
the regularized holonomy data $(R,\Phi)$ of
Definition~\textup{\ref{def:regularized-holonomy-data}} satisfy:
\begin{enumerate}[label=\textup{(\roman*)}]
\item quasi-hexagon relations on
 $\overline{\Conf}_3^{\mathrm{ord}}(\bA^1)$; and
\item the pentagon relation on the codimension-one Stasheff
 cell complex of $\overline{\Conf}_4^{\mathrm{ord}}(\bA^1)$.
\end{enumerate}
\end{theorem}

\begin{proof}
The boundary strata of
$\overline{\Conf}_3^{\mathrm{ord}}(\bA^1)$ for the
bracketings $(12)3$ and $1(23)$ admit collar neighborhoods
in which the regularized holonomy factors as the ordered
product of two-body holonomies. The comparison between
these two collar factorizations is the comparison holonomy
$\Phi(w,z)$, yielding the quasi-hexagon.
For $n = 4$, the codimension-one boundary strata of
$\overline{\Conf}_4^{\mathrm{ord}}(\bA^1)$ form the
Stasheff pentagon. Flatness of $\bD_4$ implies that the
total regularized transport around its boundary is the
identity, which is the pentagon relation.
\end{proof}

\begin{remark}[CG interpretation]
\label{rem:spectral-bridge-cg}
In the CG framework of
Conjecture~\ref{conj:ainfty-yb-consistency}, the
quasi-factorization theorem says: the MC element
$\tau \in \operatorname{Conv}(\bar B(Y), Y^!)$ is an
\emph{infinitesimal} factorization datum. Its
exponentiation to holonomy is the passage from the
convolution algebra to the factorization quantum group.
The quasi-hexagon defect $\Phi$ is the image of the
$A_\infty$ Yang--Baxter defect under this exponentiation.
\end{remark}

%% ================================================================
%% Spectral Drinfeld class and strictification
%% ================================================================
\subsubsection{The spectral Drinfeld class}

The obstruction to strictifying a quasi-factorization quantum
group into an honest one lives in a filtered cohomology theory.

\begin{definition}[Spectral cochain complex and Drinfeld class]
\label{def:spectral-drinfeld-class}
\index{Drinfeld class!spectral!definition}
Define the spectral cochain groups
\[
 C^2_{\mathrm{spec}}(A) = \{g(u) \in A^{\widehat\otimes 2}\},
 \qquad
 C^3_{\mathrm{spec}}(A) = \{\phi(w,z) \in A^{\widehat\otimes 3}\},
\]
with linearized spectral differential
\[
 (\delta g)(w,z)
 =
 1 \otimes g(z)
 + (\mathrm{id} \otimes \Delta_z)g(w)
 - (\Delta_w \otimes \mathrm{id})g(z)
 - g(w) \otimes 1.
\]
Denote the resulting cohomology by $H^3_{\mathrm{spec}}(A)$.
If
$\Phi(w,z) = 1 + \phi_n(w,z) \pmod{F^{n+1}}$
with $\phi_n$ the first nontrivial term, its class
\[
 \mathfrak{D}_{\mathrm{spec}}(A,\Omega)
 := [\phi_n]
 \in H^3_{\mathrm{spec}}(\mathrm{gr}^n A)
\]
is the \emph{spectral Drinfeld class}.
\end{definition}

\begin{theorem}[Strictification by spectral cohomology;
\ClaimStatusProvedHere]
\label{thm:spectral-strictification-cohomology}
\index{strictification!spectral cohomology}
Suppose $\Phi(w,z) = 1 + \phi_n(w,z) \pmod{F^{n+1}}$ with
$n \ge 2$. Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $\phi_n$ is a $3$-cocycle in the spectral complex;
\item under a spectral twist
 $G_n(u) = 1 + g_n(u) \pmod{F^{n+1}}$, one has
 $\phi_n \mapsto \phi_n + \delta g_n$;
\item if $[\phi_n] = 0$ in
 $H^3_{\mathrm{spec}}(\mathrm{gr}^n A)$, a twist
 kills $\phi_n$ modulo $F^{n+1}$;
\item if $H^3_{\mathrm{spec}}(\mathrm{gr}^n A) = 0$ for all
 $n \ge 2$, there exists a filtered twist~$G$ making
 $\Phi^G = 1$, and the quasi-factorization datum
 strictifies to an honest spectral factorization $R$-matrix.
\end{enumerate}
\end{theorem}

\begin{proof}
Expand the pentagon relation in the first nontrivial filtration
degree. All nonlinear terms lie in higher filtration, so
$\phi_n$ satisfies the linearized pentagon and is a cocycle.
The twist formula for the quasi-associator at degree~$n$
yields addition by $\delta g_n$. Killing the leading term
and iterating recursively proves~(iii) and~(iv).
\end{proof}

The Yangian-to-factorization bridge is a filtered obstruction problem: the passage
\[
 \text{dg-shifted Yangian}
 \;\longrightarrow\;
 \text{spectral quasi-factorization QG}
 \;\overset{\mathfrak{D}_{\mathrm{spec}}}{\longrightarrow}\;
 \text{strict factorization QG}
\]
is canonical in the first arrow and obstructed by a concrete
spectral cohomology class in the second.

%% ================================================================
%% Triangle localization: universal coefficient 1/2
%% ================================================================
\subsubsection{Low-filtration localization: universal
coefficients $\frac{1}{2}$ and $\frac{1}{3}$}

The first two filtration sectors where the spectral Drinfeld
class can be computed explicitly are the adjacent-root triangle
(filtration~$2$) and the root-quadrilateral (filtration~$3$)
sectors. Both yield universal rational coefficients.

Let $i \sim j$ be adjacent simple roots in a type-$A_2$ Levi.
Write $E_{ij} = [E_i, E_j]$ and $F_{ij} = [F_j, F_i]$, and
on three tensor factors define the left triangle vector
$T_{ij}^L = E_{ij}^{(1)} F_i^{(2)} F_j^{(3)}$.

\begin{theorem}[Triangle localization; \ClaimStatusProvedHere]
\label{thm:spectral-triangle-localization}
\index{triangle localization|textbf}
\index{universal coefficient!1/2@$1/2$}
Let
$S_{12}(w) = \rho_i(w)\,E_i^{(1)}F_i^{(2)} + \cdots$ and
$S_{13}(w+z) = \rho_j(w+z)\,E_j^{(1)}F_j^{(3)} + \cdots$.
The projection to the oriented left triangle sector of the
commutator $\frac{1}{2}[S_{12}(w), S_{13}(w+z)]$ is
\[
 \tfrac{1}{2}\,\rho_i(w)\,\rho_j(w+z)\,T_{ij}^L
 \;-\;
 \tfrac{1}{2}\,\rho_j(w)\,\rho_i(w+z)\,T_{ji}^L,
\]
with the analogous formula on the right. Under the rational
ansatz $\rho_\alpha(u) = c_\alpha/u$ with
$c_i = c_j = c_{ij} = 1$, the adjacent-root rigidity equations
\textup{(}equating coproduct and product contributions in the
hexagon\textup{)} are uniquely solved by the universal triangle
coefficient
\[
 \boxed{\;\lambda_{\mathrm{tri}} = \tfrac{1}{2}.\;}
\]
\end{theorem}

\begin{proof}
The only nonzero commutators landing in the triangle sector
are $[E_i^{(1)}F_i^{(2)}, E_j^{(1)}F_j^{(3)}] =
E_{ij}^{(1)}F_i^{(2)}F_j^{(3)}$ and its orientation reversal.
Projecting the hexagon defect to this sector and matching
coproduct contributions from the composite-root generator
$X_{ij}$ yields the displayed rigidity equations, which in the
normalized rational ansatz give $\lambda = c_i c_j / (2 c_{ij})
= 1/2$.
\end{proof}

For the next filtration, let $i \sim j \sim k$ be a chain
of simple roots of type~$A_3$ with $i$ not adjacent to~$k$.
Define $E_{ijk} = [E_{ij}, E_k] = [E_i, E_{jk}]$ and the
corresponding lowering operators, and set
$Q_{ijk}^L = E_{ijk}^{(1)} F_i^{(2)} F_j^{(3)} F_k^{(4)}$.

\begin{theorem}[Quadrilateral localization; \ClaimStatusProvedHere]
\label{thm:spectral-quadrilateral-localization}
\index{quadrilateral localization|textbf}
\index{universal coefficient!1/3@$1/3$}
The projection of
$\log\bigl(e^{X_i^{12}(u)}\, e^{X_j^{13}(u+v)}\,
e^{X_k^{14}(u+v+t)}\bigr)$
to the left quadrilateral sector is
\[
 \tfrac{1}{3}\,\rho_i(u)\,\rho_j(u+v)\,\rho_k(u+v+t)
 \;Q_{ijk}^L.
\]
The universal coefficient $\frac{1}{3}$ arises from the
class-$3$ ordered BCH formula: in a class-$3$ nilpotent Lie
algebra with $[X,Z] = 0$, the multilinear $XYZ$-part of
$\log(e^X e^Y e^Z)$ is $\frac{1}{3}[X,[Y,Z]]$. Under the
rational ansatz with $c_i = c_j = c_k = c_{ijk} = 1$, the
quadrilateral rigidity equations are uniquely solved by
\[
 \boxed{\;\lambda_{\mathrm{quad}} = \tfrac{1}{3}.\;}
\]
\end{theorem}

\begin{proof}
Since $i$ and $k$ are nonadjacent, $[X_i^{12}, X_k^{14}] = 0$.
Lemma~\ref{lem:class3-bch-spectral} below gives the
multilinear $XYZ$-part as $\frac{1}{3}[X,[Y,Z]]$. Computing
$[Y,Z] = \rho_j(u+v)\,\rho_k(u+v+t)\,E_{jk}^{(1)}
F_j^{(3)} F_k^{(4)}$ and then
$[X,[Y,Z]] = \rho_i(u)\,\rho_j(u+v)\,\rho_k(u+v+t)\,Q_{ijk}^L$
gives the localization formula. Matching with the four-body
coproduct projection and using the rational ansatz yields
$\lambda = 1/3$.
\end{proof}

\begin{lemma}[Class-$3$ ordered BCH coefficient; \ClaimStatusProvedHere]
\label{lem:class3-bch-spectral}
In a class-$3$ nilpotent Lie algebra with $[X,Z] = 0$,
\[
 \operatorname{mult}_{XYZ}\log(e^X e^Y e^Z)
 = \tfrac{1}{3}[X,[Y,Z]].
\]
\end{lemma}

\begin{proof}
Write $U = \log(e^X e^Y) = X + Y + \frac{1}{2}[X,Y]
+ \frac{1}{12}[X,[X,Y]] + \frac{1}{12}[Y,[Y,X]]$.
Then $\log(e^U e^Z) = U + Z + \frac{1}{2}[U,Z] + \cdots$,
and extracting the multilinear $XYZ$-part gives
$\frac{1}{4}[[X,Y],Z] + \frac{1}{12}[X,[Y,Z]]
+ \frac{1}{12}[Y,[X,Z]]$.
When $[X,Z] = 0$, Jacobi gives $[[X,Y],Z] = [X,[Y,Z]]$ and
the sum reduces to $\frac{1}{3}[X,[Y,Z]]$.
\end{proof}

\begin{remark}[Shift transport, not shift invariance]
\label{rem:spectral-shift-transport}
\index{shift transport!spectral}
A naive ``shift-invariance'' statement at mixed-root level is
false if interpreted coefficientwise. The shift changes local
coefficients by explicit ratios of shift characters at different
spectral arguments. What is invariant is the
\emph{obstruction class} after transport by the shift cocycle.
In particular, the shifted triangle transport coefficients
are uniquely determined by
\[
 \kappa_{ij}^{L,\mu}(w,z)
 =
 \frac{\chi_i^\mu(w)\,\chi_j^\mu(w+z)}{\chi_{ij}^\mu(w)}
 \;\kappa_{ij}^{L,0}(w,z),
\]
and the analogous quadrilateral law holds at filtration~$3$
\ifannalsedition\else
(cf.\ Remark~\ref{rem:transport-not-invariance}
in the source material)
\fi. No new independent obstruction class
appears in filtrations $2$ or~$3$.
\end{remark}

%% ================================================================
%% Cartan shift theory and exact Drinfeld class
%% ================================================================
\subsubsection{Cartan shift theory and exact Drinfeld class}

The Cartan-diagonal sector admits an explicit computation
showing that the spectral Drinfeld class is exact: the
associator defect is a coboundary.

\begin{theorem}[Cartan-diagonal Drinfeld class is exact;
\ClaimStatusProvedHere]
\label{thm:spectral-cartan-diagonal-exact}
\index{Drinfeld class!Cartan-diagonal exactness}
\index{Cartan shift!cocycle}
Let $H$ be a completed commutative primitive Cartan bialgebra
with primitive generators $h_1, \ldots, h_\ell$, and let
$\phi_i(u) = \log H_i(u)$ be the shifted Cartan currents.
Define the formal bicharacter
\[
 F_\mu(u)
 = \exp\!\Bigl(\sum_{i=1}^\ell \phi_i(u)\,h_i \otimes h_i\Bigr).
\]
Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $F_\mu(u)$ satisfies the cocycle identities
 $(\mathrm{id} \otimes \Delta)F_\mu = F_\mu^{12} F_\mu^{13}$
 and
 $(\Delta \otimes \mathrm{id})F_\mu = F_\mu^{13} F_\mu^{23}$
 \textup{(}since $\Delta h_i = h_i \otimes 1 + 1 \otimes h_i$
 and the $h_i$ commute\textup{)}.
\item The Cartan gauge twist
 $G_{\mu,n} = \exp(-S_{\mu,n})$ with
 $S_{\mu,n} = \sum_{a<b} \sum_i \phi_i(z_b - z_a)\,
 h_i^{(a)} h_i^{(b)}$
 transforms an unshifted derived KZ connection $\bD_n^0$
 into the shifted connection
 $\bD_n^\mu = G_{\mu,n}\,\bD_n^0\,G_{\mu,n}^{-1}$,
 which has connection form
 $A_n^\mu = A_n^0 + \sum_{a<b} \sum_i
 \phi_i'(z_b-z_a)\,h_i^{(a)}h_i^{(b)}\,d(z_b-z_a)$.
\item On a Cartan-diagonal line $L_\lambda$, the three-body
 quasi-hexagon defect is
 \[
 \Phi_{\mu,\lambda}^{\mathrm{sh}}(w,z)
 =
 \frac{R_{\mu,\lambda}^{\mathrm{sh}}(w+z)}
 {R_{\mu,\lambda}^{\mathrm{sh}}(w)\,
 R_{\mu,\lambda}^{\mathrm{sh}}(z)},
 \]
 whose logarithm
 $\sum_i \lambda_i^2\bigl(\phi_i(w+z) - \phi_i(w) - \phi_i(z)
 \bigr)$
 is manifestly a coboundary. Hence the Cartan-diagonal
 contribution to the spectral Drinfeld class is exact.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(i) follows from the splitting of the exponent under
the cocommutative coproduct. Part~(ii) is a direct gauge
computation using the commutation hypothesis on the Cartan
sector. Part~(iii): the defect $\phi_i(w+z) - \phi_i(w)
- \phi_i(z)$ is by definition $\delta(\phi_i)$ in the
spectral complex.
\end{proof}

The first genuine shifted examples (the framed $A_1$ shifted
Yangian and the staircase shifted Yangians of finite type~$A$,
relevant to the DK-4 frontier of
Remark~\ref{rem:modular-yangian-dk}) all have
Cartan-diagonal sectors in which the shift produces a visible
three-body logarithmic defect but no cohomological obstruction.

%% ================================================================
%% Abelian strictification and residue-bounded completion
%% ================================================================
\subsubsection{Abelian strictification and completion}

Two cases where the spectral Drinfeld class vanishes
automatically deserve separate statements.

\begin{theorem}[Abelian strictification; \ClaimStatusProvedHere]
\label{thm:spectral-abelian-strictification}
\index{strictification!abelian}
If all coefficients of the suspended kernel
$\widetilde{r}(z)$ supercommute, $m_k = 0$ for $k \ge 3$,
and the underlying coproduct is cocommutative, then
\[
 R(z) = \exp_\star(\widetilde{r}(z))
\]
converges and defines an honest spectral $R$-matrix on the
completed bialgebra underlying~$Y$.
\end{theorem}

\begin{proof}
The infinitesimal coassociativity identities exponentiate
because all coefficients commute, yielding the hexagon.
Cocommutativity gives almost cocommutativity automatically.
\end{proof}

This covers the free/$\beta\gamma$ propagator matching of
Proposition~\ref{prop:free-propagator-matching}: the abelian
kernel $r(z) = \mathbb{1} \otimes \mathbb{1}/z$ strictifies
immediately.

\begin{theorem}[Residue-bounded completion; \ClaimStatusProvedHere]
\label{thm:spectral-residue-bounded-completion}
\index{residue-bounded completion}
Let $Y = \varprojlim_N Y_N$ be residue-bounded and complete,
with each $Y_N$ quadratic-Koszul and the inverse system
$\{H^m(\bar B(Y_N))\}_N$ Mittag--Leffler. Then the completed
coderivation $D = d_B + I_{\widetilde{r}}$ converges
continuously on $\widehat{B}(Y)$, satisfies $D^2 = 0$, and
the completed cobar comparison
\[
 \Omega\widehat{B}(Y) \;\longrightarrow\; Y
\]
is a quasi-isomorphism.
\end{theorem}

\begin{proof}
Residue-boundedness ensures that on each filtration quotient only
finitely many residues contribute, so the coderivation converges.
The three-particle obstruction identity (the assertion that
$D^2|_{\text{length}\,3} = I_{\mathfrak{Y}_{\widetilde{r}}}$
with $\mathfrak{Y}_{\widetilde{r}}$ the $A_\infty$ Yang--Baxter
defect) implies $D^2 = 0$ quotientwise. Separatedness passes
this to the inverse limit. Koszulness and Mittag--Leffler
pass the quotientwise bar-cobar quasi-isomorphisms to the
completion.
\end{proof}

This is the completed version of
Remark~\ref{rem:completion-four-checks}: checks~(1)--(3)
of the Yangian tower completion are exactly the hypotheses of
Theorem~\ref{thm:spectral-residue-bounded-completion}.

%% ================================================================
%% Exact free transport
%% ================================================================
\subsubsection{The exact free model}

The free model admits a closed-form transport formula.

\begin{proposition}[Exact free transport; \ClaimStatusProvedHere]
\label{prop:spectral-exact-free-transport}
\index{free model!exact transport}
Let $\Theta(x,y) = \Psi(x) \otimes X(y) - X(x) \otimes \Psi(y)$
be the free two-body kernel.
Then $\Theta(x,y)^2 = 0$, so the connection
$\nabla_{\mathrm{free}} = d - \Theta(x,y)/(u + x - y)\,du$
integrates exactly with transport
\[
 T(u,u_0)
 = 1 + \Theta(x,y)\,\log\frac{u + x - y}{u_0 + x - y}.
\]
The local monodromy around $u + x - y = 0$ is
$M_{\mathrm{loop}} = 1 + 2\pi i\,\Theta(x,y)$.
\end{proposition}

\begin{proof}
Since $\Theta^2 = 0$, the matrix exponential truncates:
$\exp(\Theta\,\log(\cdots)) = 1 + \Theta\,\log(\cdots)$.
Differentiating gives the transport equation. The monodromy
follows from the $2\pi i$ increment of the logarithm.
\end{proof}

%% ================================================================
%% Conditional strictification criterion
%% ================================================================
\subsubsection{The conditional strictification criterion}

The preceding results assemble into a single criterion for
a shifted dg-shifted Yangian to admit a full $\Eone$-chiral
realization.

\begin{theorem}[Conditional strictification criterion;
\ClaimStatusProvedHere]
\label{thm:spectral-conditional-strictification}
\index{strictification!conditional criterion|textbf}
Let $\Ydg_\cA$ be a residue-bounded complete dg-shifted Yangian
\textup{(}Definition~\textup{\ref{def:dg-shifted-yangian}}\textup{)}.
Assume:
\begin{enumerate}[label=\textup{(C\arabic*)}]
\item\label{item:strict-C1}
 the unshifted dg object strictifies to a factorization quantum
 group with spectral $R$-matrix $R_0$
 \textup{(}i.e.\ $\mathfrak{D}_{\mathrm{spec}}(A, \Omega_0)
 = 0$\textup{)};
\item\label{item:strict-C2}
 the shift is implemented by the Cartan cocycle of
 Theorem~\textup{\ref{thm:spectral-cartan-diagonal-exact}};
\item\label{item:strict-C3}
 the infinitesimal logarithm of the shifted spectral transport
 agrees with the dg kernel after residue-bounded completion
 \textup{(}Theorem~\textup{\ref{thm:spectral-residue-bounded-completion}}\textup{)}; and
\item\label{item:strict-C4}
 the spectral Drinfeld classes
 $\mathfrak{D}_{\mathrm{spec}}(\mathrm{gr}^n A)$ vanish for
 all $n \ge 2$
 \textup{(}Theorem~\textup{\ref{thm:spectral-strictification-cohomology}}\textup{)}.
\end{enumerate}
Then the shifted dg-shifted Yangian admits a completed
$\Eone$-chiral/factorization realization whose representation
category is that of an honest spectral factorization quantum
group.
\end{theorem}

\begin{proof}
Condition~\ref{item:strict-C1} gives a strict spectral object
at the unshifted level.
Condition~\ref{item:strict-C2} transports it to a shifted
quasi-factorization datum via the Cartan gauge twist.
Condition~\ref{item:strict-C4} then allows recursive
strictification of the shifted quasi-associator
(Theorem~\ref{thm:spectral-strictification-cohomology}(iv)).
Condition~\ref{item:strict-C3} upgrades finite-stage compatibility
to the full completed statement via
Theorem~\ref{thm:spectral-residue-bounded-completion}.
\end{proof}

\begin{remark}[Status of conditions C1--C4]
\label{rem:spectral-c1c4-status}
\index{strictification!status of conditions}
For the $\mathfrak{sl}_N$ Yangian tower:
\begin{itemize}
\item \ref{item:strict-C1} holds at
 the evaluation locus by the proved DK-0/1 comparison
 (Theorem~\ref{thm:derived-dk-yangian});
 extending this to an unshifted completed strict spectral object is
 additional bridge input. B2
 (Remark~\ref{rem:completion-four-checks}) supplies the completed dg
 side of that comparison, but not by itself the full unshifted
 spectral/factorization strictification required by
 \ref{item:strict-C1}.
\item \ref{item:strict-C2} holds for all framed and staircase
 shifts by construction.
\item \ref{item:strict-C3} is the completed compatibility upgrade:
 Theorem~\ref{thm:spectral-residue-bounded-completion} promotes the
 residue-bounded finite-stage compatibility to the completed
 bar/cobar statement once a completed dg model is in hand, while on
 the standard RTT lane the H-level realization/comparison packet of
 Remark~\ref{rem:completion-four-checks} supplies the dg side of that
 comparison. Thus \ref{item:strict-C3} is not identical to
 check~(4) alone.
\item \ref{item:strict-C4} is \textbf{proved for all simple Lie algebras}
 (Volume~II, Theorem~thm:complete-strictification):
 root multiplicity one forces the spectral Drinfeld class to vanish
 at every filtration, via root-space one-dimensionality and the Jacobi
 collapse lemma. In filtrations~$2$ and~$3$, the vanishing also
 follows from the triangle and quadrilateral localization theorems.
 The true remaining frontier is Kac--Moody algebras with root
 multiplicities~$> 1$, where root-space one-dimensionality fails.
\end{itemize}
Thus, once an unshifted completed strict spectral object satisfying
\ref{item:strict-C1} is supplied, the remaining new work in the
conditional strictification criterion is the completed compatibility
package \ref{item:strict-C3}; condition \ref{item:strict-C4} is
proved unconditionally for all simple types.
\end{remark}

\begin{remark}[Relation to the DK square]
\label{rem:spectral-bridge-dk-square}
\index{Drinfeld--Kohno!DK square!spectral bridge relation}
The spectral factorization bridge provides a concrete pathway
for the B4 target of the Bridge Theorem
(Remark~\ref{rem:bridge-theorem-programme}). The DK square of
Remark~\ref{rem:dk-square-geometry} relates the $\Eone$-chiral
factorization category to the evaluation-locus quantum group.
The present construction extends this to the completed Yangian
tower: the spectral $R$-matrix from the conditional
strictification criterion is the candidate bridge datum connecting the
completed bar-cobar tower
$\Omega(\widehat{\bar B}(Y)) \xrightarrow{\sim} Y$
(Remark~\ref{rem:completion-four-checks})
to Latyntsev's factorization-quantum-group side
\cite{Latyntsev23}. Once the residual DK-4/5 extension/completion packet and the
unshifted completed strict spectral input of
Condition~\ref{item:strict-C1} are supplied, the chain
\[
 \text{$\Eone$-chiral fact.\ category}
 \;\xrightarrow{\text{DK-0..3}}\;
 \Ydg(\mathfrak{sl}_N)
 \;\xrightarrow{\text{bar-horiz.}}\;
 \text{spectral quasi-fact.\ QG}
 \;\xrightarrow{\mathfrak{D}_{\mathrm{spec}}}\;
 \text{strict fact.\ QG}
\]
becomes a concrete programme. On that conditional surface, the
remaining intrinsic strictification obstruction is concentrated in the
spectral Drinfeld class at filtration~$\ge 4$.
\end{remark}
