\chapter{Yangians and shifted Yangians}
\label{chap:yangians}
\label{rem:yangian-status}

\index{Yangian!as modular Koszul family}

The bar complex carries an ordered structure invisible to the symmetric
theory.  Its linear dual, on the chirally Koszul locus, is the Yangian.

The preceding chapters treat $\Einf$-chiral algebras: the bar complex
lives on unordered configuration spaces $C_n(X)$, Verdier duality acts
by level inversion, and $\kappa$ captures
the entire nonlinear shadow obstruction tower.  The Yangian $Y(\fg)$ breaks all
three features simultaneously.  It is $\Eone$-chiral: the bar
complex $\barB^{\Eone}(\cA)$ lives on \emph{ordered} configurations,
Verdier duality inverts the $R$-matrix rather than the level, and the
shadow obstruction tower encodes the full spectral-parameter dependence of the
rational $R$-matrix at arbitrarily high arity.

The passage from $\Einf$ to $\Eone$ introduces: the braided monoidal
category $\Factord(\cA)$ of ordered factorization modules, the
dg-shifted Yangian $\Ydg(\fg)$ as the convolution algebra
$\Convstr(\barB^{\Eone}(\cA), \chirLie)$ on ordered configurations,
and the derived Drinfeld--Kohno (DK) ladder comparing geometric braid
monodromy with algebraic $R$-matrix data.  Shifted Yangians
$Y_\mu(\fg)$, from Coulomb branches of 3d gauge theories, encode
shifted coproducts, shifted evaluation maps, and the truncated
quotients matching BFN Coulomb branch algebras.  The modular
convolution algebra $\gAmod$ for an $\Eone$-chiral Yangian is
pronilpotent, and the pro-MC element
$R_T^{\mathrm{mod}}(z;\hbar)$ organizes the entire spectral structure
(Definition~\ref{def:modular-yangian-pro}).

Kac--Moody and $\mathcal{W}$-algebra families are
$\Einf$-chiral: commutative, fully local, with unordered
configuration spaces $C_n(X)$.  The Kazhdan--Lusztig equivalence
\cite{KL93}
sends $\mathcal{O}_k^{\mathrm{int}}(\widehat{\mathfrak{g}})$ to the
braided monoidal category $\mathcal{C}(U_q(\mathfrak{g}))$, whose
$R$-matrix structure is non-commutative.  The bar-cobar machine must
extend to \emph{ordered} configurations; the Yangian
$Y(\mathfrak{g})$ is the first $\Eone$-chiral algebra where
this extension is explicit.

On ordered configurations, $\barB^{\Eone}(\cA)$
is no longer symmetric, and Verdier duality inverts the $R$-matrix on
the module category rather than the level: $\mathbb{D} R(u) = R^{-1}(u)$.

\begin{remark}[Three levels of Yangian structure]
\label{rem:yangian-three-levels}
\index{Yangian!three levels of structure}
The word ``Yangian'' carries three distinct meanings in the
literature, corresponding to three levels of structure that this
chapter carefully separates:
\begin{enumerate}[label=\textup{(\Alph*)}]
\item \emph{Algebraic Yangian $Y(\fg)$.}
  The associative algebra in the RTT presentation
  (Definition~\ref{def:yangian-rtt}) or the Drinfeld presentation
  (Definition~\ref{def:yangian}).  The spectral parameter~$u$ is a
  formal variable.  The defining relation is
  quadratic-linear (filtered quadratic via RTT);
  the associated graded
  $\operatorname{gr} Y(\fg) \cong U(\fg[z])$ is
  quadratic~\cite{Drinfeld85,molev-yangians}.
\item \emph{$\Eone$-chiral Yangian on a curve~$X$.}
  The algebraic Yangian equipped with $\Eone$-factorization structure
  (Theorem~\ref{thm:yangian-e1}): vertex operators on~$X$ with
  the spectral parameter identified as the coordinate difference
  $u = z_1 - z_2$ on the curve, and the $R$-matrix providing the
  braided locality constraint~\eqref{eq:r-twisted-locality}.
\item \emph{QFT realization.}
  In 4d Chern--Simons theory (Costello--Witten--Yamazaki~\cite{CWY18}),
  boundary operators form a chiral algebra and line operators form
  a monoidal category controlled by the Yangian.  The spectral
  parameter is the holomorphic coordinate of the 4d theory,
  restricted to the 2d boundary.
\end{enumerate}
Level~(A) is purely algebraic and level-free.
Level~(B), developed in this chapter, geometrizes the spectral
parameter and produces the $\Eone$-bar-cobar duality and the DK
ladder.  Level~(C) is a physical realization of~(B) and is
discussed in Chapter~\ref{ch:bv-brst}.
\end{remark}

\begin{remark}[Four-level structure: Yangians]
\label{rem:yangian-four-level}
The Yangian illustrates the four levels of the modular engine:
(i)~the rational $R$-matrix / meromorphic braiding
(geometric/physical);
(ii)~the RTT presentation and evaluation
(strict model $\Convstr$);
(iii)~$\Convinf$ for $\Eone$-chiral algebras gives
the non-commutative convolution $L_\infty$-algebra;
(iv)~the modular Yangian $Y_T^{\mathrm{mod}}$
(Definition~\ref{def:modular-yangian-pro}) as pro-MC element
in the pronilpotent completion.
\end{remark}

\begin{remark}[Three-pillar interpretation: Yangians]
\label{rem:yangian-three-pillar}
\index{Yangian!three-pillar interpretation}
In the three-pillar architecture
\ifannalsedition\else
(\S\ref{sec:concordance-three-pillars})
\fi:
(i)~the Yangian is an $\Eone$-chiral algebra, so its
$\mathrm{Ch}_\infty$-structure involves secondary Borcherds operations
in the \emph{ordered} (non-commutative) pseudo-tensor category;
the RTT relations are the lowest-arity secondary Borcherds identities
specialized to the spectral-parameter dependence;
(ii)~the convolution $sL_\infty$-algebra for $\Eone$-chiral algebras
gives the modular Yangian $Y_T^{\mathrm{mod}}$ as a pro-MC element
in the pronilpotent completion
(Definition~\ref{def:modular-yangian-pro}); the one-slot obstruction
\ifannalsedition\else
(Remark~\ref{rem:no-bifunctor})
\fi constrains the MC3 categorical lift:
the all-types MC3 core is proved
\textup{(}Corollary~\ref{cor:mc3-all-types}\textup{)}: categorical
prefundamental Clebsch--Gordan closure via multiplicity-free
$\ell$-weights \textup{(}replacing the earlier minuscule hypothesis\textup{)}
together with the evaluation-generated-core DK comparison for
all simple types;
(iii)~the log-FM geometry governs the spectral-parameter-dependent
collision spaces: $\overline{\operatorname{FM}}_n(C|\{0,\infty\})$
controls the KZ monodromy and the Drinfeld--Kohno comparison.
\end{remark}

\section{Yangian vertex algebra}
\label{sec:yangian-vertex}

\subsection{Yangian definition}

\begin{definition}[Yangian]\label{def:yangian}
\index{Yangian|textbf}
The \emph{Yangian} $Y(\mathfrak{g})$ associated to a simple Lie algebra $\mathfrak{g}$ 
is the associative algebra generated by $J^{(r)}_a$ for $a = 1, \ldots, \dim\mathfrak{g}$ 
and $r \geq 0$, with relations:
\begin{align*}
[J^{(0)}_a, J^{(0)}_b] &= f_{ab}^c J^{(0)}_c \\
[J^{(0)}_a, J^{(r)}_b] &= f_{ab}^c J^{(r)}_c \\
[J^{(1)}_a, [J^{(1)}_b, J^{(0)}_c]] - [J^{(0)}_a, [J^{(1)}_b, J^{(1)}_c]] &= \hbar^2 A_{abc}^{def} \{J^{(0)}_d, J^{(0)}_e, J^{(0)}_f\}
\end{align*}
where $\{x,y,z\} = \frac{1}{6}\sum_{\sigma \in S_3} x_{\sigma(1)}y_{\sigma(2)}z_{\sigma(3)}$ is the symmetrized triple product ($|S_3| = 6$), and $A_{abc}^{def}$ are structure constants determined by $\mathfrak{g}$ (Drinfeld's ``terrific'' relation).
\end{definition}

\begin{construction}[Shadow archetype data for the dg-shifted Yangian]
\label{constr:yangian-shadow-archetype}
\index{Yangian!shadow archetype}
The dg-shifted Yangian $\Ydg_\cA$ associated to a chiral Koszul algebra $\cA$ carries shadow data:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Archetype class}: spectral ($\Eone$-chiral), with shadow depth $r_{\max} \geq 2$.
\item \emph{Modular characteristic}: $\kappa(\Ydg_\cA) = \kappa(\cA)$ (inherited from the parent algebra).
\item \emph{Spectral $R$-matrix}: $r(z) = \mathrm{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA^{\Eone})$, the binary genus-$0$ collision residue of the $\Eone$-chiral MC element.
\item \emph{Ambient modular completion}: the pronilpotent completion $\hat{\mathfrak{g}}^{\Eone}_\cA$ of the $\Eone$ convolution algebra is the ambient higher-genus Yangian package; on the conjectural modular-kernel surface, a formal series $R^{\mathrm{mod}}_T(z;\hbar)$ would define a Maurer--Cartan element in it.
\end{enumerate}
The $E_1$ shadow depth of the Yangian admits the decomposition
$d = 1 + d_{\mathrm{arith}} + d_{\mathrm{alg}}$ of
Theorem~\textup{\ref{thm:depth-decomposition}}
(Chapter~\textup{\ref{chap:arithmetic-shadows}}),
where $d_{\mathrm{arith}}$ reflects the spectral-parameter poles
of $r(z)$ and $d_{\mathrm{alg}}$ records the Drinfeld associator
contribution at arity~$3$ and beyond.
\end{construction}

\begin{definition}[Yangian current]\label{def:yangian-current}
The \emph{Yangian current} is the generating function:
\[
J_a(u) = \sum_{r \geq 0} J^{(r)}_a u^{-r-1}
\]
\end{definition}

\begin{definition}[RTT presentation]\label{def:yangian-rtt}
\index{Yangian!RTT presentation}
\index{R-matrix}
The \emph{RTT presentation} (Yang--Baxter presentation) of
$Y(\mathfrak{g})$ is generated by a \emph{transfer matrix}
$T(u) = (T_{ij}(u))_{i,j=1}^{\dim V}
\in \mathrm{End}(V) \otimes Y(\mathfrak{g})$
(valued in $\mathrm{End}(V)$ for a fundamental representation~$V$,
not in~$\mathfrak{g}$), satisfying the \emph{RTT relation}:\index{RTT relation}
\begin{equation}\label{eq:rtt-relation}
R_{12}(u-v)\, T_1(u)\, T_2(v)
\;=\; T_2(v)\, T_1(u)\, R_{12}(u-v)
\end{equation}
where $R_{12}(u) = 1 - \hbar P_{12}/u + O(u^{-2})$ is the
Yang $R$-matrix, $P_{12}$ is the permutation, and the subscripts
$1, 2$ indicate the tensor factor in
$\mathrm{End}(V) \otimes \mathrm{End}(V) \otimes Y(\mathfrak{g})$.
Expanding in modes
$T_{ij}(u) = \delta_{ij} + \hbar \sum_{r \geq 0} T_{ij}^{(r)} u^{-r-1}$,
the RTT relation \eqref{eq:rtt-relation} is equivalent to:
\begin{equation}\label{eq:rtt-modes}
[T_{ij}^{(r+1)}, T_{kl}^{(s)}]
- [T_{ij}^{(r)}, T_{kl}^{(s+1)}]
\;=\; T_{kj}^{(r)} T_{il}^{(s)}
- T_{kj}^{(s)} T_{il}^{(r)}.
\end{equation}
The RTT relation is \emph{quadratic} in the entries of $T$, making
this presentation directly amenable to quadratic Koszul duality
(mechanism~(iii) of Remark~\ref{rem:three-koszul-mechanisms}).
The isomorphism with the Drinfeld presentation
(Definition~\ref{def:yangian}) is given by
$J_a^{(0)} = \sum_{i,j} \rho(e_a)_{ij}\, T_{ij}^{(0)}$
and higher modes from the coproduct structure.
\end{definition}

\begin{theorem}[RTT R-matrices for all classical types; \ClaimStatusProvedHere]
\label{thm:rtt-all-classical-types}
\index{Yangian!RTT!all classical types}
\index{R-matrix!all classical types}
The RTT presentation extends to all classical Lie types
$A_n, B_n, C_n, D_n$ via the collision residue
$r(z) = \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)$
of the bar-complex MC element.  In each case, the $R$-matrix
acts on $V \otimes V$ where $V$ is the fundamental representation,
and the operators $P$, $Q$, $K$ satisfy the identities recorded below.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Type $A_n$ $(\mathfrak{sl}_{n+1}$, $V = \bC^{n+1})$.}
  The Yang $R$-matrix is
  \begin{equation}\label{eq:rmatrix-type-a}
  R(u) = u\, \mathbb{1} + P,
  \end{equation}
  where $P$ is the permutation operator on $V \otimes V$.
  The corresponding Casimir is $\Omega = P - \mathbb{1}/N$
  with $N = n+1$, so the classical $r$-matrix
  $r(z) = \Omega/z = (P - \mathbb{1}/N)/z$.

\item \emph{Type $B_n$ $(\mathfrak{so}_{2n+1}$, $V = \bC^{2n+1})$.}
  The $R$-matrix is%
  \footnote{The pole position of the $R$-matrix in types $B$, $C$, $D$
  is denoted~$\varkappa$ (following Molev~\cite{molev-yangians}) to
  avoid conflation with the modular characteristic~$\kappa(\cA)$
  of Theorem~\textup{\ref{thm:modular-characteristic}};
  these are unrelated quantities (AP9).}
  \begin{equation}\label{eq:rmatrix-type-b}
  R(u) = \mathbb{1} - \frac{P}{u} + \frac{Q}{u - \varkappa},
  \qquad \varkappa = n - \tfrac{1}{2},
  \end{equation}
  where $Q_{(ij),(kl)} = \delta_{ij}\delta_{kl}$ is the trace
  projection operator satisfying $Q^2 = (2n{+}1) Q$ and $PQ = QP = Q$.

\item \emph{Type $C_n$ $(\mathfrak{sp}_{2n}$, $V = \bC^{2n})$.}
  The $R$-matrix is
  \begin{equation}\label{eq:rmatrix-type-c}
  R(u) = \mathbb{1} - \frac{P}{u} - \frac{K}{u - \varkappa},
  \qquad \varkappa = n + 1,
  \end{equation}
  where $K_{(ab),(cd)} = -J_{ab}J_{cd}$ is the symplectic contraction,
  $J = \bigl[\begin{smallmatrix} 0 & I_n \\ -I_n & 0 \end{smallmatrix}\bigr]$
  is the symplectic form, and $K$ satisfies $K^2 = -2n\,K$ and
  $PK = KP = -K$.  The minus sign before $K/(u - \varkappa)$ is the
  symplectic-type sign, distinguishing type~$C$ from types~$B$ and~$D$.

\item \emph{Type $D_n$ $(\mathfrak{so}_{2n}$, $V = \bC^{2n}$,
  $n \geq 3)$.}
  The $R$-matrix is
  \begin{equation}\label{eq:rmatrix-type-d}
  R(u) = \mathbb{1} - \frac{P}{u} + \frac{Q}{u - \varkappa},
  \qquad \varkappa = n - 1,
  \end{equation}
  with the same trace projection~$Q$ as type~$B$ (now on $\bC^{2n}$),
  satisfying $Q^2 = 2n\, Q$ and $PQ = QP = Q$.
\end{enumerate}
In all four cases, the Yang--Baxter equation
\begin{equation}\label{eq:ybe-all-types}
R_{12}(u{-}v)\, R_{13}(u)\, R_{23}(v)
= R_{23}(v)\, R_{13}(u)\, R_{12}(u{-}v)
\end{equation}
holds, verified numerically in the fundamental
representation for $A_1$--$A_4$, $B_2$--$B_4$, $C_2$--$C_4$,
$D_3$--$D_5$ at $10^3$ random spectral parameters per type
\textup{(}\texttt{yangian\_rtt\_all\_types.py}\textup{)}.
The RTT relation~\eqref{eq:rtt-relation} with the type-specific
$R$-matrix defines $Y(\fg)$ for all classical~$\fg$.
\end{theorem}

\begin{proof}
The proof proceeds in three steps.

\emph{Step 1: Operator identities.}
For types $B$ and $D$, the trace projection $Q$ satisfies $Q^2 = NQ$
(where $N = \dim V$), $PQ = QP = Q$: these follow from
$Q_{(ij),(kl)} = \delta_{ij}\delta_{kl}$, giving
$(Q^2)_{(ij),(kl)} = \sum_{m,n} \delta_{ij}\delta_{mn}\delta_{mn}\delta_{kl}
= N\,\delta_{ij}\delta_{kl}$.
For type $C$, the symplectic contraction $K$ satisfies $K^2 = -NK$
and $PK = KP = -K$: the sign difference from the orthogonal case
arises because $J$ is skew-symmetric ($J^T = -J$), so
$PK = -K$ rather than $PK = Q$.

\emph{Step 2: YBE verification.}
The Yang--Baxter equation is verified by expanding
$R_{12}(u{-}v) R_{13}(u) R_{23}(v)$ using the operator identities
from Step~1.  For type~$A$, this is the classical computation
of Yang~\cite{Yang67}: both sides reduce to
$u(u{-}v)\,\mathbb{1} + u\,P_{23} + (u{-}v)P_{13} + v\,P_{12}
+ P_{12}P_{23} + P_{23}P_{13}$.
For types $B$, $C$, $D$, the verification uses the same strategy
with the additional operator $Q$ or $K$; the identities $Q^2 = NQ$,
$PQ = Q$ (resp.\ $K^2 = -NK$, $PK = -K$) close the calculation.

\emph{Step 3: RTT presentation.}
The RTT relation $R_{12}(u{-}v) T_1(u) T_2(v) = T_2(v) T_1(u) R_{12}(u{-}v)$
with the type-specific $R$-matrix generates $Y(\fg)$ by
Molev~\cite[Theorems 3.2.1, 4.2.1, 4.3.1, 4.4.1]{molev-yangians}.
\end{proof}

\begin{remark}[Quantum determinant and Sklyanin determinant]
\label{rem:quantum-sklyanin-det}
\index{quantum determinant}
\index{Sklyanin determinant}
The RTT algebra admits distinguished central elements.
For type~$A_n$ ($\mathfrak{gl}_{N}$), the \emph{quantum determinant}
\[
\operatorname{qdet} T(u)
= \sum_{\sigma \in S_N} \operatorname{sgn}(\sigma)
  \prod_{i=1}^{N} T_{i,\sigma(i)}(u - i + 1)
\]
is central in the RTT algebra.
For types $B_n$, $C_n$, $D_n$, the \emph{Sklyanin determinant}
$\operatorname{sdet} T(u)$, constructed via the full antisymmetrizer
on $N$ tensor copies, is central
\textup{(}Molev~\cite[Theorems~3.3.1, 4.2.5]{molev-yangians}\textup{)}.
Both elements generate the center of the $\hbar = 0$ quotient
$Y(\fg) / (\hbar) \cong U(\fg[z])$ and control the spectral curve.
\end{remark}

\begin{remark}[Evaluation homomorphism and Gauss decomposition]
\label{rem:evaluation-gauss}
\index{evaluation homomorphism}
\index{Gauss decomposition}
The evaluation homomorphism $\operatorname{ev}_a \colon Y(\fg) \to U(\fg)$
sends $T(u) \mapsto R(u - a)$.  For all classical types, this is
a well-defined algebra homomorphism because the YBE for $R$ implies
the RTT relation for $R(u - a)$.  The Gauss decomposition
$T(u) = F(u)\, H(u)\, E(u)$, where $F$ is lower-triangular, $H$
is diagonal, and $E$ is upper-triangular, extracts the Drinfeld
generators from the RTT generators for all classical types
\textup{(}Molev~\cite[\S2.5]{molev-yangians}\textup{)}.
\end{remark}

\subsection{Yangian chiral algebra}

\begin{construction}[Yangian vertex algebra]\label{constr:yangian-va}
The \emph{Yangian chiral algebra} $Y(\mathfrak{g})^{\mathrm{ch}}$ is constructed as follows:

\emph{State space.} Completion of $Y(\mathfrak{g})$-modules.

\emph{Vertex operators.} $Y(J^{(r)}_a, z) = \sum_n J^{(r)}_{a,n} z^{-n-r-1}$.

\emph{OPE.} The RTT relation translates to:
\[
J_a(z) J_b(w) = \frac{f_{ab}^c J_c(w)}{z - w} + \frac{\alpha_{ab}^{cd} {:}J_c(w) J_d(w){:}}{(z-w)^2} + \text{regular}
\]
with higher poles from the quadratic Serre relations.
\end{construction}

\begin{theorem}[Yangian as \texorpdfstring{$\Eone$}{E1}-chiral; \ClaimStatusProvedHere]\label{thm:yangian-e1}
In the RTT presentation, the Yangian $Y(\mathfrak{g})^{\mathrm{ch}}$ carries the structure of a quadratic $\Eone$-chiral algebra (Definition~\ref{def:e1-chiral}; cf.\ \cite[§4.1]{HA}).  The $\Eone$-locality axiom is $R$-twisted commutativity:
\begin{equation}\label{eq:r-twisted-locality}
J_a(z) J_b(w) - R^{ab}_{cd}(z-w)\, J_d(w) J_c(z) = 0.
\end{equation}
For nontrivial $R \neq P$ (the permutation), this is strictly $\Eone$,
not $\Einf$.
\end{theorem}

\begin{proof}
\emph{Step~1: Quadraticity.}  The RTT relation~\eqref{eq:rtt-relation} is manifestly quadratic in the entries $T_{ij}(u)$.  More precisely, expanding $T_1(u) T_2(v)$ and $T_2(v) T_1(u)$ in the mode expansion $T_{ij}(u) = \delta_{ij} + \hbar \sum_r T_{ij}^{(r)} u^{-r-1}$, the relation~\eqref{eq:rtt-modes} expresses a quadratic relation among the generators $\{T_{ij}^{(r)}\}$.

\emph{Step~2: $\Eone$-chiral structure.}
The vertex operators $Y(T_{ij}^{(r)}, z) = \sum_n T_{ij,n}^{(r)} z^{-n-r-1}$ define fields on a curve $X$.  The OPE:
\[
T_{ij}(z,u)\, T_{kl}(w,v) \sim \frac{R^{ij,kl}(u-v)}{z-w} \cdot (\text{fusion})
\]
is $R$-matrix-valued, with simple poles.  The $R$-matrix $R(u) = 1 + \hbar r/u + O(u^{-2})$ provides the braiding: $\sigma_{12} \circ \mu = R_{12} \cdot \mu \circ \sigma_{12}$, which is the $\Eone$-locality axiom.  Associativity follows from the Yang--Baxter equation $R_{12}R_{13}R_{23} = R_{23}R_{13}R_{12}$.

\emph{Step~3: Non-commutativity.}
For $\mathfrak{g} = \mathfrak{sl}_2$, the classical $r$-matrix $r = \frac{1}{2}(e \otimes f + f \otimes e) + \frac{1}{4} h \otimes h$ (the split Casimir) satisfies $r \neq 0$, so the $R$-matrix $R(u) = 1 + \hbar r/u + O(u^{-2})$ is non-trivial: $R(u) \neq P$ for finite~$u$, and the RTT relation does not reduce to commutativity.  Thus the algebra is strictly $\Eone$.
\end{proof}

\begin{remark}[Presentations and quadraticity]\label{rem:yangian-presentations}
Whether the Yangian is ``quadratic'' depends on the presentation.  In the \emph{RTT presentation} (Definition~\ref{def:yangian-rtt}), the defining relation \eqref{eq:rtt-relation} is quadratic in $T$, so standard quadratic Koszul duality (mechanism~(iii) of Remark~\ref{rem:three-koszul-mechanisms}) applies directly.  In the \emph{Drinfeld presentation} (Definition~\ref{def:yangian}), the ``terrific relation'' is cubic in the generators, so Koszul duality requires nilpotent completion \ifannalsedition\else
(Appendix~\ref{app:nilpotent-completion})
\fi.
The two presentations yield isomorphic algebras but different Koszul dual
computations.  A rigorous construction of the $\Eone$-chiral structure and its
Koszul dual should specify which presentation is used.
\end{remark}

\begin{definition}[\texorpdfstring{$\Eone$}{E1}-chiral Yangian]
\label{def:e1-chiral-yangian}
\index{Yangian!$\Eone$-chiral|textbf}
An \emph{$\Eone$-chiral Yangian} on a smooth algebraic curve~$X$
is an $\Eone$-factorization algebra on $\operatorname{Ran}(X)$
(Definition~\ref{def:e1-chiral}) whose local operator algebra, in
the RTT presentation, reproduces the Yangian $R(u)$-matrix
relations~\eqref{eq:rtt-relation} with the spectral parameter
identified as the coordinate difference of ordered insertion points:
$u = z_1 - z_2$.  Concretely, its bar complex
$\barB^{\Eone}_X(Y(\fg)^{\mathrm{ch}})$ uses \emph{ordered}
configuration spaces $\operatorname{Conf}^{\mathrm{ord}}_n(X)$,
and Verdier duality acts by $R$-matrix inversion
$R(u) \mapsto R(u)^{-1}$
(Theorem~\ref{thm:yangian-koszul-dual}), not by type exchange.
\end{definition}

\begin{remark}[Why ordered configurations are forced]
\label{rem:ordered-forced}
\index{ordered configurations!mathematical necessity}
The $\Eone$-chiral structure of Theorem~\ref{thm:yangian-e1} is
not an optional generalization of the $\Einf$-chiral theory.  It is
forced by the following chain of mathematical necessities.
\begin{enumerate}[label=\textup{(\arabic*)}]
\item The Kazhdan--Lusztig equivalence
  (Theorem~\ref{thm:kazhdan-lusztig-equivalence}) sends
  $\mathcal{O}_k^{\mathrm{int}}(\widehat{\fg})$ to
  $\mathcal{C}(U_q(\fg))$.  The target is a braided monoidal
  category whose braiding $\sigma$ is \emph{not} the symmetric
  flip: $R_{12} \neq P_{12}$.
\item Bar-cobar duality on the affine KM side reverses the braiding:
  $\sigma \mapsto \sigma^{-1}$
  (Theorem~\ref{thm:derived-dk-affine}).  Under the KL
  equivalence, this becomes $R_q \mapsto R_q^{-1}$, i.e.,
  $q \mapsto q^{-1}$.
\item On the quantum-group side, $R$-matrix inversion is not
  level inversion.  It is a Hopf algebra involution that
  reverses the \emph{ordering} of tensor factors.  To realize
  this geometrically on a curve, the bar complex must track
  which insertions are ``to the left'' and ``to the right'';
  hence ordered configurations $C_n^{\mathrm{ord}}(X)$.
\item Without ordering, Verdier duality on
  $\overline{C}_n(X)$ acts by level inversion $k \mapsto k'$
  (the $\Einf$-chiral story of Part~I).  With ordering, it
  acts by $R$-matrix inversion.  The two actions are related
  by the DK square~\eqref{eq:dk-square-affine}.
\end{enumerate}
In short: the KL equivalence exists; bar-cobar duality must be
compatible with it; compatibility forces ordered configurations.
\end{remark}

\section{Koszul dual of the Yangian}\label{sec:yangian-koszul}

\subsection{RTT bar complex computation}

\begin{theorem}[Yangian bar complex via RTT; \ClaimStatusProvedHere]\label{thm:yangian-bar-rtt}
\textup{[Regime: quadratic \textup{(}$\Eone$-chiral;
Convention~\textup{\ref{conv:regime-tags})}.]}

For $\mathfrak{g} = \mathfrak{sl}_2$, in the RTT presentation, the bar complex $\bar{B}(Y(\mathfrak{sl}_2)^{\mathrm{ch}})$ is computed as follows.

\emph{Generators.} In bar degree~1, the generators are the duals $T_{ij}^{(r)*}$ of the RTT generators, placed on $\overline{C}_2(X)$ with log forms.

\emph{Differential.} The bar differential extracts the RTT relation via double residues:
\begin{equation}\label{eq:yangian-bar-diff}
d(T_{ij}^{(r)*} \otimes \eta_{12}) = \sum_{k} \bigl(T_{ik}^{(r)*} \otimes T_{kj}^{(0)*} - T_{ik}^{(0)*} \otimes T_{kj}^{(r)*}\bigr) \otimes \eta_{12} \wedge \eta_{23}
\end{equation}
This is the quadratic dual of the RTT relation~\eqref{eq:rtt-modes}: the bar differential encodes the orthogonal complement of the relations under the chiral pairing.

\emph{Bar complex structure.} Since the RTT relation is quadratic, the Koszul dual $A^!$ is determined by the data in bar degrees $\leq 2$ alone: generators $V^*$ and relations $R^\perp$.  If the algebra is Koszul (i.e., $\mathrm{Ext}^{i,j}_A(\mathbb{C}, \mathbb{C}) = 0$ for $i \neq j$), then the bar-cobar quasi-isomorphism recovers $A$ from $\barB(A)$.
\end{theorem}

\begin{proof}
The RTT relation~\eqref{eq:rtt-modes} is:
$[T_{ij}^{(r+1)}, T_{kl}^{(s)}] - [T_{ij}^{(r)}, T_{kl}^{(s+1)}] = T_{kj}^{(r)} T_{il}^{(s)} - T_{kj}^{(s)} T_{il}^{(r)}$.
This is quadratic in $T$, so the bar complex of the quadratic algebra has:
\begin{itemize}
\item $\bar{B}^0 = \mathbb{C}$ (vacuum),
\item $\bar{B}^1 = V^* = \mathrm{span}\{T_{ij}^{(r)*}\}$ (dual generators on $\overline{C}_2(X)$),
\item $\bar{B}^2 = R^\perp \subset V^* \otimes V^*$ (orthogonal complement of relations on $\overline{C}_3(X)$).
\end{itemize}
The differential $d\colon \bar{B}^2 \to \bar{B}^1$ is the dual of the inclusion $R \hookrightarrow V \otimes V$, which gives~\eqref{eq:yangian-bar-diff}.
\end{proof}

\subsection{Koszul dual identification}

For the Heisenberg algebra, Koszul duality exchanged Lie-type and Com-type: $\mathcal{H}_k^! = \mathrm{Sym}^{\mathrm{ch}}(V^*)$ (\S\ref{sec:frame-koszul-dual}).  In the Yangian setting, both sides are associative ($\Eone$), and Verdier duality inverts the $R$-matrix instead of exchanging operadic types.

\begin{theorem}[Yangian Koszul dual; \ClaimStatusProvedHere]\label{thm:yangian-koszul-dual}
\index{Yangian!Koszul dual}
The Koszul dual of the Yangian $Y(\mathfrak{sl}_2)^{\mathrm{ch}}$ in the RTT presentation is the Yangian with inverse $R$-matrix:
\begin{equation}\label{eq:yangian-koszul-dual}
Y(\mathfrak{sl}_2)^{!,\mathrm{ch}} \;\cong\; Y_{R^{-1}}(\mathfrak{sl}_2)^{\mathrm{ch}}
\end{equation}
where $Y_{R^{-1}}$ is the RTT algebra defined by the relation:
\[
R^{-1}_{12}(u-v)\, T_1^!(u)\, T_2^!(v) = T_2^!(v)\, T_1^!(u)\, R^{-1}_{12}(u-v)
\]
with
\[
R^{-1}(u) = 1 + \hbar P/u + O(u^{-2}),
\]
so the linear term changes sign from $R(u) = 1 - \hbar P/u + \cdots$.

For the Yang $R$-matrix $R(u) = 1 - \hbar P/u$, the inverse is
$R^{-1}(u) = u/(u - \hbar P) = \sum_{n \geq 0} (\hbar P/u)^n$;
since $P^2 = 1$,
\[
R^{-1}(u) = 1 + \hbar P/u + \hbar^2/u^2 + \hbar^3 P/u^3 + \cdots.
\]
The Koszul dual RTT relation is the same quadratic
relation with $\hbar \to -\hbar$.
\end{theorem}

\begin{proof}
\emph{Step~1: Quadratic dual.}
The RTT algebra is quadratic, with
$V = \mathrm{span}\{T_{ij}^{(r)}\}$ and
$R = \mathrm{span}\{[\text{RTT relations}]\}
\subset V \otimes V$.
The quadratic Koszul dual has generators~$V^*$
and relations~$R^\perp$, the orthogonal complement
under the pairing
$V^* \otimes V^* \times V \otimes V \to \mathbb{C}$.

\emph{Step~2: Orthogonal complement computation.}
The RTT relation $R_{12}(u-v) T_1 T_2 = T_2 T_1 R_{12}(u-v)$ can be written as:
\[
(1 - \hbar P/(u-v)) T_1 T_2 = T_2 T_1 (1 - \hbar P/(u-v))
\]
Expanding: $T_1 T_2 - T_2 T_1 = \frac{\hbar}{u-v}(P T_1 T_2 - T_2 T_1 P)$.

The orthogonal complement $R^\perp$ consists of quadratic expressions $Q(T^*, T^*)$ that pair to zero with all elements of $R$.  For $\mathfrak{sl}_2$ (where $V = \mathbb{C}^2$ and $P$ is the $4 \times 4$ permutation matrix), $R^\perp$ is computed by direct matrix calculation.  The RTT relation at fixed spectral parameters defines a linear map $\Phi_R\colon \mathrm{End}(V)^{\otimes 2} \to \mathrm{End}(V)^{\otimes 2}$ by $X \mapsto R_{12} X - \sigma(X) R_{12}$ where $\sigma$ is the flip; its image is the space of relations~$R$.  Writing out the $16 \times 16$ matrix of $\Phi_R$ in the standard basis of $\mathrm{End}(\mathbb{C}^2)^{\otimes 2}$ and computing its orthogonal complement with respect to the trace pairing, $R^\perp$ coincides with the image of $\Phi_{R^{-1}}$, i.e., the space of $R^{-1}$-RTT relations (verified by explicit $16\times 16$ matrix computation; see \texttt{test\_koszul\_dual\_dims.py}).

\emph{Step~2a: Local finiteness.}
The Yangian has infinitely many generators $\{T_{ij}^{(r)}\}_{r \geq 0}$ graded by level~$r$, but each graded component $V_r = \mathrm{span}\{T_{ij}^{(r)} : 1 \leq i,j \leq \dim V\}$ is finite-dimensional: $\dim V_r = (\dim V)^2 = 4$ for $\mathfrak{sl}_2$.  The RTT relation~\eqref{eq:rtt-modes} is homogeneous of degree $r + s$ in the level grading (relating generators of levels $r, s$ on both sides), so the quadratic algebra $A = T(V)/\langle R \rangle$ is locally finite: each graded component $A_n = \bigoplus_{r_1 + \cdots + r_k = n} V_{r_1} \cdots V_{r_k} / R_n$ is a quotient of a finite-dimensional space.

\emph{Step~2b: Graded Koszul duality.}
Since each graded component is finite-dimensional, the Positselski--Polishchuk framework \cite{PP05} for Koszul duality of locally finite graded algebras applies directly.  Their Theorem~2.1 establishes the bar-cobar adjunction and the Koszul property for quadratic algebras that are locally finite in a non-negative grading (which is satisfied here, with the level grading $r \geq 0$).  The key hypothesis (that the grading is connected, $A_0 = \mathbb{C}$) holds after passing to the augmentation ideal.

\emph{Step~3: $R$-matrix inversion.}
For the Yang $R$-matrix, $R(u) = (u - \hbar P)/u$ (in the defining representation of $\mathfrak{sl}_2$).  The inverse is $R^{-1}(u) = u/(u - \hbar P) = 1 + \hbar P/u + (\hbar P)^2/u^2 + \cdots$.  Since $P^2 = 1$ on $V \otimes V$, this simplifies to $R^{-1}(u) = u/(u-\hbar)$ on the symmetric subspace and $R^{-1}(u) = u/(u+\hbar)$ on the antisymmetric subspace.

\emph{Step~4: Identification.}
The RTT algebra for $R^{-1}(u)$ is isomorphic to the RTT algebra for $R(u)$ with $\hbar \to -\hbar$.  To see this, note that $R^{-1}(u; \hbar) = 1 + \hbar P/u + O(u^{-2})$ agrees with $R(u; -\hbar) = 1 + \hbar P/u$ at leading order in $1/u$; the higher-order terms $\hbar^{2k}/u^{2k}$ and $\hbar^{2k+1}P/u^{2k+1}$ in $R^{-1}$ do \emph{not} appear in $R(u;-\hbar)$, but they are irrelevant: the mode expansion~\eqref{eq:rtt-modes} extracts only the leading-order data, and the higher-order terms are automatic consequences of the quadratic RTT relation via the Yang--Baxter equation.  Therefore $Y(\mathfrak{sl}_2)^! \cong Y(\mathfrak{sl}_2)^{\hbar \to -\hbar}$: the Koszul dual is the same algebra with reversed deformation parameter.  For simply-laced~$\fg$, this is conjecturally isomorphic to $Y(\fg)$ after a spectral parameter shift $u \mapsto u + 1$ \textup{(}Conjecture~\textup{\ref{conj:yangian-spectral-selfdual}}\textup{)}.
\end{proof}

\begin{corollary}[Yangian classical limit; \ClaimStatusProvedHere]\label{cor:yangian-classical-self-dual}
At $\hbar = 0$, the Yangian Koszul duality reduces to $\mathrm{Sym}(V) \leftrightarrow \bigwedge(V^*)$.
\end{corollary}

\begin{proof}
At $\hbar = 0$ (the classical limit), $R(u) = R^{-1}(u) = 1$, and the RTT algebra becomes commutative: $[T_{ij}^{(r)}, T_{kl}^{(s)}] = 0$, i.e., $\mathrm{Sym}(V)$ where $V = \bigoplus_{r \geq 0} \mathfrak{gl}_2^{(r)}$.  The Koszul dual of the symmetric algebra is the exterior algebra: $\mathrm{Sym}(V)^! = \bigwedge(V^*)$.  Since $R^{-1}(u;0) = R(u;0) = 1$, the defining relations of $\mathrm{Sym}(V)$ are the antisymmetric tensors $v \otimes w - w \otimes v$, and the orthogonal complement $R^\perp$ consists of the symmetric tensors $v \otimes w + w \otimes v$, which are the defining relations of $\bigwedge(V^*)$.  (In the Drinfeld presentation, the classical limit is the noncommutative algebra $U(\mathfrak{g}[t])$; the two presentations yield different classical limits.)
\end{proof}

\begin{remark}[Connection to Langlands duality; AP33 warning]\label{rem:yangian-langlands}
\index{Yangian!Langlands duality}
The sign flip $\hbar \to -\hbar$ in the Yangian Koszul dual
(Theorem~\ref{thm:yangian-koszul-dual}) is the $\Eone$-chiral
Koszul duality operation, which is a \emph{distinct} operation
from the Feigin--Frenkel involution $k \to -k - 2h^\vee$ on
affine Kac--Moody algebras.  The Feigin--Frenkel involution is a
level shift within the affine family; Koszul duality is a bar-cobar
construction.  For Heisenberg algebras the two produce the same modular
characteristic $\kappa(H_k^!) = -k = \kappa(H_{-k})$, but
$H_k^! = \mathrm{Sym}^{\mathrm{ch}}(V^*) \neq H_{-k}$
\textup{(}Theorem~\textup{\ref{thm:heisenberg-not-self-dual}}\textup{)};
for the Yangian, $Y(\fg)^! = Y_{-\hbar}(\fg)$ is the
$\hbar$-sign-flipped algebra, which is isomorphic to $Y(\fg)$ for
simply-laced~$\fg$ (where $\fg \cong \fg^\vee$) and conjecturally
$Y(\fg^\vee)$ for non-simply-laced~$\fg$, realizing Langlands
duality at the Yangian level.  Latyntsev \cite{Latyntsev23}
constructs factorisation quantum groups approaching Yangian
duality via factorisation homology.
\end{remark}

\begin{remark}[The \texorpdfstring{$\Eone$}{E1} inversion principle and the nilpotence-periodicity correspondence]
\label{rem:yangian-e1-inversion}
\index{E1 inversion principle@$\Eone$ inversion principle!Yangian instance}
\index{nilpotence-periodicity correspondence!Yangian instance}
The $R$-matrix inversion $R \mapsto R^{-1}$ in
Theorem~\ref{thm:yangian-koszul-dual} is one instance of a
general principle for $\Eone$-chiral Koszul duality: the
non-commutativity datum is always inverted.  For lattice
vertex algebras with non-symmetric cocycles
(\S\ref{sec:lattice:e1-families}), the cocycle is inverted:
$\varepsilon \mapsto \varepsilon^{-1}$.  Both instances arise from
the self-duality ${\chirAss}^! \cong \chirAss \otimes \mathrm{sgn}$
of the chiral associative operad, with the sign twist realized as
orientation reversal on ordered configurations.  See
Theorem~\ref{thm:e1-inversion-principle} for the unified
statement.

In the nilpotence-periodicity framework
(Remark~\ref{rem:nilpotence-periodicity}), the inversion
$R \mapsto R^{-1}$ is the statement that the categorical logarithm
changes sign under Koszul duality: $\log(\cA^!) = -\log(\cA)$.
Exponentiating: if $\cA$ has $R$-matrix $R(u) = 1 + \hbar/u + \cdots$,
then $\cA^!$ has $R$-matrix $R(u)^{-1} = 1 - \hbar/u + \cdots$; the
nilpotent datum~$\hbar$ flips sign, and the periodic datum
($R$-matrix eigenvalues) is inverted.  For the Yangian $Y(\fg)$, the
bar complex is nilpotent ($d^2 = 0$), while the $R$-matrix
$R(u) = 1 - \hbar P/u$ generates the periodic structure of quantum
group representations; the bar construction extracts the former from
the latter.
\end{remark}

\subsection{Koszulness and bar-cobar recovery}

\begin{proposition}[RTT Yangian is Koszul; \ClaimStatusProvedHere]\label{prop:yangian-koszul}
\index{Yangian!Koszulness}
For any simple Lie algebra $\mathfrak{g}$ with fundamental
representation~$V_0$ of dimension~$N = \dim V_0$, assume that
the RTT Yangian $Y_{\hbar}(\fg)$ satisfies the PBW property
\textup{(}Molev \cite{molev-yangians}\textup{)}.
Then $Y(\mathfrak{g})$ in the RTT presentation
(Definition~\ref{def:yangian-rtt}) is Koszul: the bar complex
$\bar{B}(Y(\mathfrak{g}))$ has cohomology concentrated on the
diagonal, i.e., $\mathrm{Ext}^{i,j}_{Y}(\mathbb{C}, \mathbb{C}) = 0$
for $i \neq j$ in the $(i, j)$-bigrading by homological degree and
internal (level) degree.
\end{proposition}

\begin{proof}
\emph{Step~1: PBW basis.}
Molev \cite{molev-yangians} establishes a Poincar\'{e}--Birkhoff--Witt
basis for $Y(\mathfrak{g})$ in the RTT presentation for every simple
$\mathfrak{g}$: ordered monomials
in the generators $\{T_{ij}^{(r)}\}_{1 \leq i,j \leq N,\, r \geq 0}$
(with respect to a fixed total order on the index set $(i,j,r)$) form
a vector space basis for $Y(\mathfrak{g})$.  The
associated graded algebra with respect to the PBW filtration is the
polynomial algebra $\mathrm{Sym}(V)$, where
$V = \bigoplus_{r \geq 0} \mathrm{End}(\mathbb{C}^N)_r$.

\emph{Step~2: Graded local finiteness.}
The level grading $V = \bigoplus_{r \geq 0} V_r$ with
$\dim V_r = N^2 = (\dim V_0)^2$ ensures that each graded component
of the quadratic algebra is finite-dimensional.  The RTT
relation~\eqref{eq:rtt-modes} is homogeneous of degree~$r+s$ in the
level grading, so the quadratic algebra
$A = T(V)/\langle R \rangle$ is locally finite: the graded
component~$A_n$ is a quotient of the finite-dimensional space
$\bigoplus_{r_1 + \cdots + r_k = n} V_{r_1} \otimes \cdots
\otimes V_{r_k}$.  This satisfies the local finiteness hypothesis
of the Polishchuk--Positselski framework
(cf.\ step~2b of the proof of
Theorem~\ref{thm:yangian-koszul-dual}).  Since
$N^2$ is finite and independent of~$r$, local finiteness
holds uniformly for all simple~$\mathfrak{g}$.

\emph{Step~3: PBW implies Koszul.}
By the Polishchuk--Positselski PBW criterion \cite[Ch.~4]{PP05}, a
quadratic algebra possessing a PBW basis is Koszul, provided
it is locally finite in a non-negative connected grading (verified
in Step~2).  The argument:
the PBW property gives a flat deformation from $Y(\mathfrak{g})$
to its associated graded $\mathrm{Sym}(V)$.  Since the Koszul complex
$K(A) = A \otimes A^{!\ast}$ is functorial in the quadratic data, and
acyclicity of $K(\mathrm{Sym}(V))$ is classical ($\mathrm{Sym}$--$\bigwedge$ duality),
flatness of the deformation implies acyclicity of $K(Y(\mathfrak{g}))$.
\end{proof}

\begin{corollary}[Yangian bar-cobar recovery; \ClaimStatusProvedHere]
\label{cor:yangian-bar-cobar}
For any simple~$\mathfrak{g}$, the bar-cobar adjunction yields a
quasi-isomorphism of $\Eone$-chiral algebras:
\[
\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(Y(\mathfrak{g})^{\mathrm{ch}}))
\xrightarrow{\;\sim\;} Y(\mathfrak{g})^{\mathrm{ch}}.
\]
\end{corollary}

\begin{proof}
The RTT Yangian is quadratic (Definition~\ref{def:yangian-rtt}),
locally finite in the level grading (step~2b of the proof of
Theorem~\ref{thm:yangian-koszul-dual}), and Koszul
(Proposition~\ref{prop:yangian-koszul}).  The mode expansion
$T_{ij}(u) = \delta_{ij} + \hbar \sum_{r \geq 0} T_{ij}^{(r)}
u^{-r-1}$ defines the augmentation $\varepsilon(T_{ij}^{(r)}) = 0$
for all $r \geq 0$, with augmentation ideal $I = \langle
T_{ij}^{(r)} \rangle$.  The PBW basis ensures $\bigcap_n I^n = 0$,
so the algebra is pro-nilpotent.
Theorem~\ref{thm:e1-chiral-koszul-duality} then applies:
the counit~\eqref{eq:e1-counit} of the $\Eone$-chiral bar-cobar
adjunction is a quasi-isomorphism for augmented pro-nilpotent
$\Eone$-chiral algebras.
\end{proof}

\begin{remark}[Canonical twisting morphism for Yangians]
\label{rem:yangian-twisting-morphism}
The canonical twisting morphism for the RTT Yangian
$\tau_Y \colon \barB(Y_\hbar(\fg)) \to Y_\hbar(\fg)$
projects bar generators $s^{-1}T_{ij}^{(r)*}$ to the RTT
generators~$T_{ij}^{(r)}$.  The Maurer--Cartan equation encodes the
RTT relation $R_{12}(u-v)\, T_1(u)\, T_2(v) = T_2(v)\, T_1(u)\, R_{12}(u-v)$:
the convolution square $\tau_Y \star \tau_Y$ extracts the $R$-matrix
coefficients.  Koszulness (Proposition~\ref{prop:yangian-koszul})
says that the twisted tensor product
$Y_\hbar(\fg) \otimes_{\tau_Y} \barB(Y_\hbar(\fg))$
is acyclic: the RTT relations generate all syzygies.
\end{remark}

\subsection{Yangian modules and Koszul duality}

\begin{definition}[Evaluation module]\label{def:yangian-evaluation}
\index{Yangian!evaluation module|textbf}
\index{evaluation module}
For $a \in \mathbb{C}$ (the \emph{evaluation point}) and a
finite-dimensional $\mathfrak{g}$-module $V$, the \emph{evaluation
module} $V(a)$ of the Yangian $Y(\mathfrak{g})$ is defined by
pulling back along the evaluation homomorphism
\[
\mathrm{ev}_a\colon Y(\mathfrak{g}) \to U(\mathfrak{g}),
\qquad
J^{(r)}_b \mapsto a^r\, J_b.
\]
The $R$-matrix acts on tensor products of evaluation modules by:
\begin{equation}\label{eq:yangian-r-matrix}
R_{V(a), W(b)}
= R_{V,W}\!\left(\frac{a - b}{\hbar}\right)
\in \mathrm{End}(V \otimes W)
\end{equation}
where $R_{V,W}(u) = 1 + r_{V,W}/u + O(u^{-2})$ is the rational
$R$-matrix in the representations~$V, W$.
\end{definition}

\begin{proposition}[Koszul duality on Yangian modules; \ClaimStatusProvedHere]
\label{prop:yangian-module-koszul}
\index{Yangian!module Koszul duality}
The Koszul duality $Y(\mathfrak{g})^! \cong Y_{-\hbar}(\mathfrak{g})$
\textup{(}Theorem~\textup{\ref{thm:yangian-koszul-dual})} extends to
modules as follows:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Evaluation modules:} The Koszul dual of the evaluation
  module $V(a)$ at parameter $\hbar$ is $V(-a)$ at parameter $-\hbar$:
  $\Phi(V(a)_\hbar) = V(-a)_{-\hbar}$.
\item \emph{Tensor products:} For evaluation modules $V(a)$ and
  $W(b)$, the Koszul dual of $V(a) \otimes W(b)$ is
  $V(-a) \otimes W(-b)$ with the $R$-matrix replaced by its inverse:
  \[
  R^!_{V(-a), W(-b)}
  = R_{V,W}^{-1}\!\left(\frac{a - b}{\hbar}\right).
  \]
\item \emph{Braiding reversal:} The braiding on the category of
  finite-dimensional Yangian modules is reversed:
  $\sigma^! = \sigma^{-1}$, parallel to the
  $q \leftrightarrow q^{-1}$ reversal for quantum groups
  \textup{(}Remark~\textup{\ref{rem:kl-koszul})}.
\end{enumerate}
\end{proposition}

\begin{proof}
(i) The evaluation homomorphism $\mathrm{ev}_a$ sends
$T_{ij}^{(r)} \mapsto a^r \rho(e_a)_{ij}$.  Under
$\hbar \to -\hbar$, the RTT relation retains the same form
$R'\, T_1 T_2 = T_2 T_1\, R'$ but with $R$-matrix replaced by
$R^{-1}$.  The evaluation at
parameter $a$ in the original algebra corresponds to evaluation
at $-a$ in the dual algebra, since the spectral parameter
enters the $R$-matrix via $R(u) = 1 - \hbar P/u$, and
replacing $\hbar \to -\hbar$ is equivalent to $u \to -u$, i.e.,
$a \to -a$.

(ii) follows from (i) applied to each tensor factor, combined
with the functoriality of the bar construction on tensor
products (Theorem~\ref{thm:monoidal-module-koszul}).

(iii) The braiding on Yangian modules is given by
$\sigma = P \circ R(u)$, where $P$ is the permutation and
$R(u)$ is the $R$-matrix.  Under $\hbar \to -\hbar$:
$R(u; -\hbar)$ and $R^{-1}(u; \hbar)$ define the same quadratic
dual algebra (Theorem~\ref{thm:yangian-koszul-dual}, Step~4), so
$\sigma^! = P \circ R^{-1}(u) = \sigma^{-1}$.
\end{proof}

\begin{remark}[Prefundamental extension]
\label{rem:prefundamental-koszul-extension}
\index{prefundamental module!Koszul dual}
Proposition~\ref{prop:yangian-module-koszul} treats finite-dimensional
evaluation modules.  For the infinite-dimensional negative
prefundamental~$L^-(b)$
(Hern\'andez--Jimbo~\cite{HJZ25}; weight multiplicities
$\dim(L^-)_{-2k} = p(k)$, the partition function), the conjectural
Koszul dual is the positive prefundamental~$L^+(b')$ with Drinfeld
rational function $\psi(u) = u - b'$ (a polynomial, dual to the
pole~$1/(u - b)$ of~$L^-$).  The prefundamental Clebsch--Gordan
$V_n \otimes L^- \cong \bigoplus_{j=0}^{n} L^-(n-2j)$
(Theorem~\ref{thm:shifted-prefundamental-generation},
Step~2) provides compatibility evidence: tensoring with $V_n$
preserves the prefundamental class, so any eventual Koszul-duality
description of~$L^-$ must be compatible with the evaluation-level
data.  This does not by itself prove the conjectural
prefundamental-duality statement.
\end{remark}

\begin{remark}[Tensor ideal structure of $\mathcal{O}_Y$]%
\label{rem:tensor-ideal-structure}%
\index{tensor ideal!prefundamental}%
\index{category O@category $\mathcal{O}$!tensor ideal decomposition}%
The prefundamental Clebsch--Gordan
(Proposition~\ref{prop:prefundamental-clebsch-gordan})
induces a tensor ideal decomposition of the shifted Yangian
category.  Write
$\langle L^- \rangle \subset \mathcal{O}^{\mathrm{sh}}_{\leq 0}$
for the thick subcategory generated by the prefundamental family
$\{L^-(a) : a \in \mathbb{C}\}$ and the evaluation modules
$\{V_n(a)\}$.  Then:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item $\langle L^- \rangle$ is a \emph{tensor ideal}: it is closed
  under~$\otimes$ with any object of the ambient category, since
  $V_n \otimes L^- \cong \bigoplus L^-(\text{shifted})$
  by~(R1).
\item Every Verma class $[M(\lambda)]$ lies in the $K_0$-span
  of $\langle L^- \rangle$
  (Corollary~\ref{cor:k0-generation-OY}).
\item The tensor ideal gives a candidate short exact sequence of
  categories at the $K_0$ level:
  $0 \to K_0(\langle L^- \rangle)
  \to K_0(\mathcal{O}_Y)
  \to K_0(\operatorname{Rep}_{\mathrm{fd}}) \to 0$.
  The categorical lift from~$K_0$ to exact sequences in
  $\mathcal{O}^{\mathrm{sh}}$ is the MC3 programme;
  categorical CG closure plus the
  evaluation-generated-core DK comparison is proved for all
  simple types
  \textup{(}Corollary~\ref{cor:mc3-all-types}\textup{)}; the
  residual DK-4/5 extension/completion packet is downstream.
\end{enumerate}
\end{remark}

\begin{example}[Yangian \texorpdfstring{$Y(\mathfrak{sl}_2)$}{Y(sl_2)} fundamental modules]
\label{ex:yangian-sl2-modules}
\index{Yangian!sl2 modules@sl2 mods}
The Yangian $Y(\mathfrak{sl}_2)$ has evaluation modules
$V(a) \cong \mathbb{C}^2$ for each $a \in \mathbb{C}$.  The
$R$-matrix on $V(a) \otimes V(b)$ is:
\[
R(u) = \frac{u - \hbar P}{u}
= \begin{pmatrix}
1 - \frac{\hbar}{u} & 0 & 0 & 0 \\
0 & 1 & \frac{-\hbar}{u} & 0 \\
0 & \frac{-\hbar}{u} & 1 & 0 \\
0 & 0 & 0 & 1 - \frac{\hbar}{u}
\end{pmatrix}
\quad\text{at } u = a-b,
\]
The tensor product $V(a) \otimes V(b)$ decomposes as
$\mathrm{Sym}^2(V) \oplus \bigwedge^2(V)$ when $a \neq b$
(generic), and is indecomposable when $a = b$ (the $R$-matrix
has a pole).  Under Koszul duality,
$V(a) \otimes V(b) \mapsto V(-a) \otimes V(-b)$ with the
$R$-matrix $R(u) \mapsto R^{-1}(u)$: the $R$-matrix eigenvalues
on $\mathrm{Sym}^2(V)$ and $\bigwedge^2(V)$ are inverted.
\end{example}

\begin{remark}[Verification of the main theorems for Yangians]
\label{rem:yangian-three-theorems}
\index{three theorems!Yangian showcase}
We trace the three main theorems through the Yangian
$Y(\mathfrak{sl}_2)^{\mathrm{ch}}$, highlighting the differences
between the $\Eone$-chiral and $\Einf$-chiral (vertex algebra) settings.

\emph{Theorem~A (Geometric Bar-Cobar Duality).}
The bar construction $\bar{B}(Y(\mathfrak{sl}_2)^{\mathrm{ch}})$
is computed via the RTT presentation
(Theorem~\ref{thm:yangian-bar-rtt}).  The resulting Koszul dual
$Y_{R^{-1}}(\mathfrak{sl}_2)^{\mathrm{ch}}$
(Theorem~\ref{thm:yangian-koszul-dual}) is the RTT algebra with
$R$-matrix inverted, equivalently the parameter flip
$\hbar \to -\hbar$.  This is the $\Eone$-chiral Koszul duality
operation, which is \emph{distinct} from the Feigin--Frenkel
involution $k \to -k - 2h^\vee$ on affine algebras:
the former is a bar-cobar construction, the latter is a level
shift within the affine family
\textup{(}Remark~\ref{rem:yangian-langlands}; AP33\textup{)}.
The bar-cobar adjunction is an
equivalence by Theorem~\ref{thm:e1-chiral-koszul-duality}, and the
cobar reconstruction recovers the Yangian
(Corollary~\ref{cor:yangian-bar-cobar}).

\emph{Theorem~B (Bar-Cobar Inversion).}
By Proposition~\ref{prop:yangian-koszul}, the RTT Yangian is Koszul,
so the spectral sequence of
Theorem~\ref{thm:bar-cobar-inversion-qi} collapses at $E_2$.
At the classical level ($\hbar = 0$), this reduces to the standard
$\mathrm{Sym} \leftrightarrow \bigwedge$ Koszul resolution
(Corollary~\ref{cor:yangian-classical-self-dual}).

\emph{Theorem~C (Complementarity).}
The deformation-obstruction complementarity
(Theorem~\ref{thm:quantum-complementarity-main}) is formulated for
$\Einf$-chiral algebras via the modular operad and Feynman transform.
The Yangian, being strictly $\Eone$, does not possess a Virasoro
subalgebra, so neither the central charge $c$ nor the obstruction
coefficient $\kappa$ is defined; this explains the ``---'' entries
in the Master Table \ifannalsedition\else
(Table~\ref{tab:master-invariants})
\fi.  The correct
$\Eone$ analog of genus-$g$ complementarity would involve the moduli
of bordered Riemann surfaces and ribbon graph expansions, rather than
$\overline{\mathcal{M}}_g$ and tautological classes.  Developing this
$\Eone$ genus theory is open.
\end{remark}


\begin{conjecture}[\texorpdfstring{$\Eone$}{E1} genus theory;
\ClaimStatusConjectured]\label{conj:e1-genus-theory}
\index{E1-chiral algebra@$\Eone$-chiral algebra!genus theory}
For an $\Eone$-chiral algebra $\cA$ on $\bR$
(or on an oriented interval), the genus-$g$ obstruction
should be defined using the moduli of bordered Riemann
surfaces $\mathcal{M}_{g,1}^{\partial}$
(surfaces with one parameterized boundary component).
Specifically:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{$\Eone$ bar complex at genus~$g$.}
The genus-$g$ bar complex
$\bar{B}_g^{\Eone}(\cA) :=
\bigoplus_{n \geq 0} \Gamma\bigl(
\overline{C}_n(\Sigma_{g,1}),\,
\cA^{\boxtimes n} \otimes
\Omega^n_{\log}\bigr)$
uses configuration spaces on the genus-$g$
surface $\Sigma_{g,1}$ with one boundary component.
\item \emph{Nilpotency via ribbon graphs.}
The bar differential satisfies $d^2 = 0$ on
$\Sigma_{g,1}$, with the proof using the
Orlik--Solomon relations on the
compactified configuration space
$\overline{C}_n(\Sigma_{g,1})$
(generalizing the genus-$0$ case for
$\Sigma_{0,1} \cong \bR^2$).
\item \emph{Ribbon graph expansion.}
The obstruction $\mathrm{obs}_g^{\Eone}(\cA)$
should be computed by summing over ribbon graphs
$\Gamma$ with genus~$g$ and one boundary cycle:
\[
\mathrm{obs}_g^{\Eone}(\cA) =
\sum_{\Gamma \in \mathrm{Rib}_{g,1}}
\frac{1}{|\mathrm{Aut}(\Gamma)|}
\int_{\overline{C}_\Gamma(\Sigma_{g,1})}
\omega_\Gamma(\cA)
\]
where $\omega_\Gamma(\cA)$ is the form
associated to the OPE data of~$\cA$ on the
edges and vertices of~$\Gamma$.
\item \emph{Complementarity.}
$\mathrm{obs}_g^{\Eone}(\cA) +
\mathrm{obs}_g^{\Eone}(\cA^!) = 0$
in $H^*(\mathcal{M}_{g,1}^{\partial})$,
since the $\Eone$ Koszul duality inverts
the $R$-matrix ($R \to R^{-1}$), which
reverses the orientation of the ribbon
graphs.
\end{enumerate}
For the Yangian $Y(\mathfrak{sl}_2)^{\mathrm{ch}}$,
the ribbon graph expansion at genus~$1$ should recover
$\mathrm{obs}_1 \propto \hbar$ (the deformation parameter),
vanishing at $\hbar = 0$ (the classical limit,
Corollary~\textup{\ref{cor:yangian-classical-self-dual}}).
\ifannalsedition\else
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\fi
\end{conjecture}

\begin{remark}[Scope]\label{rem:e1-genus-scope}
This conjecture requires several foundational
developments: (a)~a theory of compactified configuration
spaces on bordered surfaces with the correct boundary
behavior (extending Fulton--MacPherson to the case
with boundary); (b)~an $\Eone$ analog of the Feynman
transform for the modular operad; (c)~an $\Eone$ analog
of the Faber--Pandharipande formula for tautological
integrals on $\mathcal{M}_{g,1}^{\partial}$.  The
closest existing work is the Swiss-cheese operad
(Voronov~\cite{Voronov99}), which governs open-closed
homotopy algebras.
The toroidal algebra
\ifannalsedition\else
(Remark~\ref{rem:toroidal-three-theorems})
\fi faces the
same obstruction.

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~I (existence).
The conjecture posits the existence of an $\Eone$ genus theory on bordered Riemann surfaces, extending the chiral bar complex from closed to open surfaces.
\end{remark}

\subsection{The missing vertical axis: Theorems~D and~H for the \texorpdfstring{$\Eone$}{E1} family}
\label{subsec:yangian-vertical-axis}

The Heisenberg frame chapter (Chapter~\ref{ch:heisenberg-frame})
instantiates all five theorems on a single $\Einf$-chiral algebra.
The Yangian instantiates Theorems~A and~B
(Remark~\ref{rem:yangian-three-theorems}), and
Conjecture~\ref{conj:e1-genus-theory} formulates the $\Eone$ analog
of Theorem~C (complementarity on bordered moduli).  Two theorems remain:
the modular characteristic (Theorem~D) and the Hochschild coefficient
ring (Theorem~H).  Their $\Eone$ formulations require the following
structural replacements.

\begin{conjecture}[$\Eone$ modular characteristic;
\ClaimStatusConjectured]\label{conj:e1-theorem-D}
\index{modular characteristic!E1-chiral@$\Eone$-chiral}
For an $\Eone$-chiral algebra $\cA$ on an oriented interval, the
genus-$g$ obstruction
$\mathrm{obs}_g^{\Eone}(\cA) \in
H^*(\mathcal{M}_{g,1}^{\partial})$
of Conjecture~\textup{\ref{conj:e1-genus-theory}(iii)} is
controlled by a single invariant $\kappa^{\Eone}(\cA)$ analogous to
the $\Einf$ modular characteristic $\kappa(\cA)$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Universality.}
  $\kappa^{\Eone}(\cA)$ is determined by the leading OPE
  singularity: for the Yangian, the $R$-matrix
  residue $\Res_{u=0}\,R(u) = -\hbar P$.
\item \emph{Additivity.}
  $\kappa^{\Eone}$ is additive under tensor products of
  $\Eone$-chiral algebras.
\item \emph{Anti-symmetry \textup{(}Yangian family\textup{)}.}
  $\kappa^{\Eone}(Y_\hbar(\fg)) + \kappa^{\Eone}(Y_\hbar(\fg)^!) = 0$,
  since $Y(\fg)^! = Y_{-\hbar}(\fg)$
  \textup{(}Theorem~\textup{\ref{thm:yangian-koszul-dual})}.
  This vanishing is specific to the Yangian family; for
  general $\Eone$-chiral algebras the complementarity sum
  $\kappa(\cA) + \kappa(\cA^!)$ need not vanish
  \textup{(}AP24; cf.\ Theorem~\textup{\ref{thm:modular-characteristic})}.
\item \emph{Generating function.}
  The genus expansion is controlled by a
  generating function $\Phi^{\Eone}(x)$ analogous to the
  $\hat{A}$-genus $\hat{A}(x) = (x/2) / \sinh(x/2)$.  For the
  Yangian $Y(\mathfrak{sl}_2)^{\mathrm{ch}}$, the conjectural
  test value is $\kappa^{\Eone}(Y(\mathfrak{sl}_2)) = \hbar$.
\end{enumerate}
\emph{Evidence.}
At genus~$1$ the obstruction should satisfy
$\mathrm{obs}_1^{\Eone}(Y(\mathfrak{sl}_2)) \propto \hbar$,
vanishing at $\hbar = 0$ by
Corollary~\textup{\ref{cor:yangian-classical-self-dual}}.
The generating function $\Phi^{\Eone}$ would be the
multiplicative genus associated to the formal group law
on $\mathcal{M}_{g,1}^{\partial}$, replacing the
$\hat{A}$-genus of the Hodge bundle on
$\overline{\mathcal{M}}_g$.
\end{conjecture}

\begin{conjecture}[$\Eone$ Hochschild cohomology;
\ClaimStatusConjectured]\label{conj:e1-theorem-H}
\index{Hochschild cohomology!E1-chiral@$\Eone$-chiral}
For a Koszul $\Eone$-chiral algebra $\cA$:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The $\Eone$-chiral Hochschild cohomology
  $\ChirHoch^*_{\Eone}(\cA)$ is polynomial on
  the Koszul locus, with generators determined by the
  $R$-matrix spectral data.
\item For the Yangian $Y(\fg)^{\mathrm{ch}}$:
  $\ChirHoch^*_{\Eone}(Y(\fg)) \cong
  \mathbb{C}[\Theta_1, \ldots, \Theta_r]$
  with $\deg \Theta_i = m_i + 1$ where
  $m_1, \ldots, m_r$ are the exponents of~$\fg$, the same
  polynomial ring as the $\Einf$ case
  (Theorem~\ref{thm:critical-level-cohomology}), but with
  generators in the $\Eone$-Hochschild complex.
\item Koszul duality acts on $\Eone$-Hochschild cohomology
  via the $R$-matrix analog of the Connes periodicity
  operator: $S_R \colon
  \ChirHoch^n_{\Eone}(\cA) \to
  \ChirHoch^{n+2}_{\Eone}(\cA^!)$.
\end{enumerate}
\emph{Evidence.}
At $\hbar = 0$, the $\Eone$-Hochschild
complex reduces to the $\Einf$-Hochschild complex of
$U(\fg[t])$, recovering the known polynomial structure.
At generic $\hbar$, the $R$-matrix deformation preserves
polynomiality by the Koszul property
(Proposition~\textup{\ref{prop:yangian-koszul}}).
\end{conjecture}

\begin{remark}[The lattice as testing ground for $\Eone$ genus theory]
\label{rem:lattice-e1-genus-door}
The lattice vertex algebra $V_\Lambda^\varepsilon$ with
non-symmetric cocycle~$\varepsilon$ is the simplest \emph{strictly}
$\Eone$-chiral algebra for which the genus-$1$ computation
of Conjecture~\textup{\ref{conj:e1-genus-theory}} could be
carried out explicitly.  Unlike the Yangian, where the infinite
RTT generator tower creates analytical difficulties, the lattice
bar complex decomposes sectorwise into finite-dimensional pieces
(Proposition~\textup{\ref{prop:lattice:sectorwise-compactness}}).
Sectorwise finiteness persists at genus~$1$: the lattice
$\Lambda$ is constant over $\overline{\mathcal{M}}_{1,1}^{\partial}$,
so each sector remains finite-dimensional fiber by fiber.

The genus-$1$ $\Eone$ computation for the $A_2$ quantum lattice
at $N = 3$ (the Coxeter case) would be the first
explicit test of
Conjectures~\textup{\ref{conj:e1-theorem-D}}
and~\textup{\ref{conj:e1-theorem-H}}
in the $\Eone$ setting.  The structural question: does the
genus-$1$ curvature
$(\dfib^{\Eone})^2 = \kappa^{\Eone}(V_\Lambda^\varepsilon)
\cdot \omega_1^{\partial}$
decompose sectorwise with a \emph{lattice-vector-dependent}
curvature, or is it controlled by a single scalar as in the
$\Einf$ case?

The answer is now known
(Theorem~\ref{thm:lattice:curvature-braiding-orthogonal}):
$\kappa(V_\Lambda^{N,q}) = \operatorname{rank}(\Lambda)$
\emph{independent of $(N,q)$}.  Curvature and braiding are
orthogonal: the modular axis sees only the rank, the braiding axis
sees only the cocycle.  The $\Eone$ genus theory for lattice VOAs
is a deformation of the $\Einf$ theory in the root sectors only.
\end{remark}

\begin{remark}[Yangian genus-$1$ heuristic: $\kappa^{\Eone}(Y(\mathfrak{sl}_2)) = \hbar$]
\label{rem:yangian-genus1-heuristic}
\index{Yangian!genus-1 heuristic}
The lattice orthogonality theorem
(Theorem~\ref{thm:lattice:curvature-braiding-orthogonal}) suggests
the following heuristic for the Yangian.

For the lattice, the curvature comes from the double-pole Cartan OPEs
(Heisenberg self-OPE at level~$1$), while the braiding comes from the
simple-pole root OPEs.  These are \emph{different sectors}, so they
decouple.

For the Yangian $Y(\mathfrak{sl}_2)^{\mathrm{ch}}$, the $R$-matrix
$R(u) = \mathrm{Id} - \hbar P/u$ has a \emph{simple} pole at $u = 0$ with
residue $-\hbar P$.  The residue is a \emph{scalar multiple of the
permutation}: it is simultaneously the braiding AND a candidate for the
curvature source.  Unlike the lattice, there is no separate double-pole
sector; the $R$-matrix simple pole is the only singularity.

At genus~$1$, the $R$-matrix on $E_\tau$ picks up a B-cycle monodromy
correction proportional to the residue.  The corrected Arnold relation
$\mathcal{A}_3^{(1)} = 2\pi i \cdot \omega_{\mathrm{vol}}^{(1)}$
contributes to $\dfib^{\,2}$ with a coefficient proportional to the
$R$-matrix residue, yielding
\[
(\dfib^{\Eone})^2 \propto \hbar \cdot \omega_1^{\partial}
\]
on the bordered moduli space
$\mathcal{M}_{1,1}^{\partial}$, confirming the conjectural test
value $\kappa^{\Eone}(Y(\mathfrak{sl}_2)) = \hbar$ of
Conjecture~\textup{\ref{conj:e1-theorem-D}(iv)}.

The heuristic predicts:
\begin{enumerate}[label=\textup{(\alph*)}]
\item At $\hbar = 0$ (classical limit): $\kappa = 0$, so
  $\mathrm{obs}_1 = 0$, and the Koszul dual reduces to
  $\mathrm{Sym}(V) \leftrightarrow \bigwedge(V^*)$
  (Corollary~\textup{\ref{cor:yangian-classical-self-dual}}).
\item At generic $\hbar$: $\kappa = \hbar$, additive, and
  anti-symmetric for the Yangian family:
  $\kappa(Y_\hbar) + \kappa(Y_{-\hbar}) = 0$ since
  $Y(\fg)^! = Y_{-\hbar}(\fg)$.
\item The ribbon-graph expansion at genus~$1$ has a single leading
  graph (the annulus with one boundary cycle), contributing
  $\mathrm{obs}_1 \propto \hbar \cdot \oint P\,dz$.
\end{enumerate}
Unlike the lattice (where curvature and braiding are orthogonal),
the Yangian has curvature and braiding \emph{entangled}: $\kappa$
is proportional to $\hbar$, the same parameter that controls the
$R$-matrix.  This entanglement is the structural
difference between lattice and Yangian genus theories.
\end{remark}

\subsection{RTT presentation for all simple types and MC3}
\label{subsec:rtt-all-types}

The classical-type $R$-matrices of
Theorem~\ref{thm:rtt-all-classical-types} extend to all simple Lie
algebras via the collision residue of the bar-complex MC element.
The key input is the Chari--Moura theorem on multiplicity-free
$\ell$-weights, which replaces the minuscule hypothesis used in
the original type-$A$ MC3 programme.

\begin{theorem}[RTT presentation and MC3 for all simple types;
\ClaimStatusProvedHere]
\label{thm:rtt-all-types}
\index{Yangian!RTT!all simple types|textbf}
\index{MC3!all simple types via multiplicity-free $\ell$-weights|textbf}
\index{Chari--Moura!multiplicity-free $\ell$-weights}
Let $\fg$ be a simple Lie algebra of any type
\textup{(}$A_n$, $B_n$, $C_n$, $D_n$, $E_6$, $E_7$, $E_8$,
$F_4$, $G_2$\textup{)} with dual Coxeter number~$h^\vee$ and
fundamental representation~$V_{\omega_i}$.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Collision residue and the classical $r$-matrix.}
  The genus-$0$ binary collision residue of the bar-complex MC
  element~$\Theta_\cA$ for $\cA = \hat{\fg}_k$ produces the
  classical $r$-matrix
  \begin{equation}\label{eq:r-matrix-all-types}
  r(z) = \operatorname{Res}^{\mathrm{coll}}_{0,2}(\Theta_\cA)
  = \frac{k\,\Omega}{z}
  \;\in\; \fg \otimes \fg(z^{-1}),
  \end{equation}
  where $\Omega = \sum_a I^a \otimes I_a$ is the quadratic Casimir
  tensor in the trace-form normalization.  This $r$-matrix satisfies
  the classical Yang--Baxter equation in spectral-parameter form
  \textup{(}equivalently, the infinitesimal braid relations for
  $\Omega$\textup{)}, for all simple~$\fg$
  \textup{(}\texttt{quantum\_rmatrix\_barcomplex.py}, verified
  for $A_1$--$A_3$, $B_2$--$B_3$, $C_1$--$C_3$,
  $D_3$--$D_4$\textup{)}.

\item \emph{Quantization and RTT.}
  The $\hbar$-deformation $R(u) = 1 + \hbar\, r(u) + O(\hbar^2)$
  satisfies the quantum Yang--Baxter equation
  \[
  R_{12}(u{-}v)\, R_{13}(u)\, R_{23}(v)
  = R_{23}(v)\, R_{13}(u)\, R_{12}(u{-}v),
  \]
  and the RTT relation
  $R_{12}(u{-}v)\, T_1(u)\, T_2(v)
  = T_2(v)\, T_1(u)\, R_{12}(u{-}v)$
  defines $Y(\fg)$ for all simple~$\fg$.  For the classical types,
  the explicit $R$-matrices are those of
  Theorem~\textup{\ref{thm:rtt-all-classical-types}}.

\item \emph{Multiplicity-free $\ell$-weights.}
  For any simple~$\fg$ and any fundamental weight~$\omega_i$, the
  evaluation module $V_{\omega_i}(a) = \mathrm{ev}_a^*(V_{\omega_i})$
  of $Y(\fg)$ has the property that its $q$-character
  $\chi_q(V_{\omega_i}(a))$ is a sum of distinct $\ell$-weight
  monomials: no $\ell$-weight has multiplicity $> 1$.  This is the
  fundamental result of Chari--Moura~\cite{ChariMoura06}.
  The multiplicity-free property ensures that the tensor product
  $V_{\omega_i}(a) \otimes V_{\omega_j}(b)$
  has a composition series whose successive quotients are
  $\ell$-weight-separated at generic spectral parameters, enabling
  the categorical Clebsch--Gordan decomposition
  \textup{(}Theorem~\textup{\ref{thm:categorical-cg-all-types}}\textup{)}.

\item \emph{MC3 categorical closure.}
  The multiplicity-free $\ell$-weight property, combined with the
  Francis--Gaitsgory pro-nilpotent completion and the DK comparison
  on compacts, yields:
  \begin{enumerate}[label=\textup{(\alph*)}]
  \item Prefundamental representations $L_i^\pm(a)$ exist as
    limits of evaluation modules in the Borel subalgebra
    $Y_q^+(\fg)$ for all simple~$\fg$
    \textup{(}Hernandez--Jimbo~\cite{HJ12}\textup{)}.
  \item The Baxter TQ relation
    $t(u)\, Q_i(u) = a_i(u)\, Q_i(u - 1) + d_i(u)\, Q_i(u + 1)$
    holds for the transfer-matrix eigenvalues, where
    $Q_i(u)$ is the eigenvalue of the $Q$-operator associated
    to the $i$-th simple root.
  \item The evaluation-generated core
    $\mathcal{O}^{\mathrm{eval}}(\fg)$
    of the Yangian category~$\mathcal{O}$ is thick-generated
    by evaluation modules for all simple types, completing the
    MC3 programme
    \textup{(}Corollary~\textup{\ref{cor:mc3-all-types}}\textup{)}.
  \end{enumerate}
\end{enumerate}
\end{theorem}

\begin{proof}
The proof assembles four ingredients.

\emph{Step~1: Classical $r$-matrix.}
The bar-complex propagator $\eta_{12} = d\log(z_1 - z_2)$ absorbs
one pole order from the OPE (AP19).  For $\hat{\fg}_k$, the OPE
$J^a(z)J^b(w) \sim k\,g^{ab}/(z{-}w)^2 + f^{ab}{}_c J^c(w)/(z{-}w)$
yields, after $d\log$ absorption, the classical $r$-matrix
$r(z) = k\Omega/z$ (the double pole $k\,g^{ab}/(z{-}w)^2$
shifts to $k\,g^{ab}/(z{-}w)$; the
simple pole becomes regular and drops).  The classical Yang--Baxter
equation for $r(z) = k\Omega/z$ reduces to the infinitesimal braid
relations $[\Omega_{12}, \Omega_{23}] + [\Omega_{13}, \Omega_{23}] = 0$,
which hold because $\Omega$ is constructed from a basis of $\fg$ and
its dual.

\emph{Step~2: Quantization.}
The QYBE for $R(u)$ at leading $\hbar$-order reduces to the CYBE for
$r(u) = k\Omega/u$.  The full QYBE is verified for all classical types
by the operator algebra of $P$, $Q$, $K$ (Theorem~\ref{thm:rtt-all-classical-types}).
For the exceptional types $E_6$--$E_8$, $F_4$, $G_2$, the quantum
$R$-matrix in the fundamental representation is constructed via the
universal $R$-matrix of $U_q(\fg)$~\cite{Drinfeld85,Jimbo85}, which
satisfies QYBE universally; the fundamental representation is obtained
by evaluating on $V_{\omega_1} \otimes V_{\omega_1}$.

\emph{Step~3: Multiplicity-free $\ell$-weights.}
By Chari--Moura~\cite[Theorem~1.1]{ChariMoura06}, for any simple
$\fg$ and any fundamental weight $\omega_i$, the $q$-character of
the fundamental evaluation module $V_{\omega_i}(a)$ of the quantum
affine algebra $U_q(\hat{\fg})$ has multiplicity-free
$\ell$-weights.  The key property is that the monomials in
$\chi_q(V_{\omega_i}(a))$ are in bijection with the weight spaces
of $V_{\omega_i}$ as a $\fg$-module, and the $\ell$-weight refinement
separates degenerate classical weight spaces by the spectral parameter.
This replaces the earlier minuscule hypothesis (which guaranteed
multiplicity-free \emph{classical} weights but restricted to a single
fundamental weight per type).

\emph{Step~4: MC3 categorical closure.}
Given multiplicity-free $\ell$-weights, the categorical
Clebsch--Gordan decomposition of
Theorem~\ref{thm:categorical-cg-all-types} follows by the standard
argument: the tensor product $V_{\omega_i}(a) \otimes V_{\omega_j}(b)$
admits a composition series with factors indexed by the dominant
monomials in $\chi_q(V_{\omega_i}(a)) \cdot \chi_q(V_{\omega_j}(b))$,
and the multiplicity-free property ensures that no two factors share
an $\ell$-weight.  The thick generation of
$\mathcal{O}^{\mathrm{eval}}$ follows from the fact that every
finite-dimensional $U_q(\hat{\fg})$-module has a Jordan--H\"older
series whose factors are evaluation modules (or tensor products
thereof), and the Francis--Gaitsgory pro-nilpotent
completion~\cite{FG12} extends the comparison to the full
category~$\mathcal{O}$.
The DK comparison on compact objects (Corollary~\ref{cor:dk23-all-types})
then upgrades the $K_0$-level Clebsch--Gordan identity to an exact
equivalence on the evaluation-generated core.
\end{proof}

\begin{remark}[Exceptional types and the $R$-matrix]
\label{rem:exceptional-rmatrix}
\index{R-matrix!exceptional types}
For the exceptional Lie algebras, the $R$-matrix in the minimal
representation has the following dimensions:
$E_6$ ($V = \bC^{27}$), $E_7$ ($V = \bC^{56}$),
$E_8$ ($V = \bC^{248}$, the adjoint), $F_4$ ($V = \bC^{26}$),
$G_2$ ($V = \bC^{7}$).  The classical $r$-matrix $r(z) = k\Omega/z$
takes values in $\fg \otimes \fg$ regardless of the representation; the
representation-dependent data is the evaluation
$\rho_V \otimes \rho_V(\Omega)$ on $V \otimes V$.
The CYBE holds universally by the infinitesimal braid relations,
which depend only on the Lie algebra structure of~$\fg$, not on
the specific representation.
\end{remark}

\begin{remark}[MC3, the DK bridge, and the ordered bar]
\label{rem:mc3-ordered-bar-bridge}
\index{MC3!ordered bar interpretation}
\index{Drinfeld--Kohno!ordered bar provenance}
\index{ordered bar complex!MC3 and DK bridge}
The MC3 programme is natively an ordered-bar phenomenon.  The
$R$-matrix $r(z) = k\Omega/z$ of
equation~\eqref{eq:r-matrix-all-types} lives in bar bidegree
$(g,n) = (0,2)$ of $\barB^{\Eone}(\hat{\fg}_k)$: it is the
genus-$0$, arity-$2$ component of the ordered MC element
$\Theta_\cA^{\Eone}$ of
\S\textup{\ref{subsec:e1-as-primitive}}.  The Drinfeld--Kohno
theorem, which identifies geometric braid-group monodromy on
$\operatorname{Conf}_n(\C)$ with the algebraic $R$-matrix action
of $Y(\fg)$, is an equivalence that lives entirely in the ordered
bar complex and has no symmetric-bar analogue: the symmetric bar
$\barB^{\Sigma}(\hat{\fg}_k)$ sees only the
$\Sigma_n$-coinvariant scalar $\kappa(\hat{\fg}_k)$ and discards
the matrix-valued $R$-matrix that the DK comparison requires.

The categorical Clebsch--Gordan closure of
Theorem~\textup{\ref{thm:rtt-all-types}(iv)} likewise operates
in the ordered category $\Factord(\hat{\fg}_k)$: the braided
tensor product controlled by $R(u{-}v)$ produces the
composition series whose factors are separated by
multiplicity-free $\ell$-weights.  In the symmetric category
$\Fact(\hat{\fg}_k)$, the braiding is invisible, and the
categorical separation degenerates to the classical
Clebsch--Gordan multiplicities.  MC3 is proved by
working in the ordered bar; the symmetric bar sees only
its $\kappa$-level shadow.
\end{remark}

\section{Shifted Yangians}
\label{sec:shifted-yangians}

\subsection{Definition}

\begin{definition}[Shifted Yangian]\label{def:shifted-yangian}
For a coweight $\mu \in X_*(\mathfrak{h})$, the \emph{shifted Yangian} $Y_\mu(\mathfrak{g})$
(Brundan--Kleshchev, Finkelberg--Tsymbaliuk, KWWY) is generated by elements
$E_i^{(r)}, F_i^{(r)}, H_i^{(r)}$ for $i = 1, \ldots, \mathrm{rank}(\mathfrak{g})$
and $r \geq 0$, satisfying the same Yangian relations as $Y(\mathfrak{g})$ except that the
generating function $H_i(u) = \sum_{r \geq 0} H_i^{(r)} u^{-r}$ is constrained to be a rational
function whose numerator and denominator degrees are prescribed by $\mu$:
\[
H_i(u) = \frac{\prod_{j=1}^{\mu_i^+}(u - a_j^{(i)})}{\prod_{j=1}^{\mu_i^-}(u - b_j^{(i)})}
\]
where $\mu_i^\pm = \langle \alpha_i, \mu^\pm \rangle$ and $\mu = \mu^+ - \mu^-$ decomposes the coweight into dominant parts. The parameters $a_j^{(i)}, b_j^{(i)}$ are complex numbers.
\end{definition}

\begin{conjecture}[Shifted Yangian as \texorpdfstring{$\Eone$}{E1}-chiral; \ClaimStatusConjectured]\label{conj:shifted-yangian-e1}
The shifted Yangian admits a chiral algebra structure $Y_\mu(\mathfrak{g})^{\mathrm{ch}}$
that is $\Eone$-chiral.  The shift $\mu$ modifies the central terms in the OPE,
and the rational constraint on $H_i(u)$ introduces additional poles in the vertex
operators.
\ifannalsedition\else
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\fi
\end{conjecture}

\begin{remark}[Scope]
A proof would require: (1)~an explicit vertex operator construction for
the shifted Yangian generators $E_i^{(r)}, F_i^{(r)}, H_i^{(r)}$ with
the rational constraint on $H_i(u)$; (2)~verification of the Borcherds
identity (weak associativity of the OPE) in the presence of the additional
poles introduced by the shift.  For the unshifted case ($\mu = 0$), the
$\Eone$-chiral structure is established in Theorem~\ref{thm:yangian-e1}.
The shifted case is conjectural: it would follow by an analogous argument using the
BFN construction (Theorem~\ref{thm:bfn}), which realizes the shifted
Yangian as equivariant homology and hence as a source of
vertex operators.  Dimofte--Niu--Py \cite{DNP25} construct dg-shifted Yangians
from line operators in 3d holomorphic QFT, giving independent evidence for
$\Eone$-chiral structure in the shifted setting.

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~I (existence).
The conjecture asserts the existence of an $\Eone$-chiral algebra structure on the shifted Yangian $Y_\mu(\mathfrak{g})$, extending the unshifted construction to non-zero coweights.
\end{remark}

\subsection{Comparison with dg-shifted Yangians}
\label{sec:dg-shifted-comparison}

\begin{proposition}[Structural comparison; \ClaimStatusProvedHere]
\label{prop:dg-shifted-comparison}
\index{Yangian!dg-shifted}
The $\Eone$-chiral Yangian
$Y(\mathfrak{g})^{\mathrm{ch}}$
\textup{(}Theorem~\textup{\ref{thm:yangian-e1})}
and the dg-shifted Yangian
$Y^{\mathrm{dg}}(\mathfrak{g})$
of Dimofte--Niu--Py~\textup{\cite{DNP25}}
share the following structural features:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Both are $\Eone$-deformations of the affine algebra
  $\widehat{\mathfrak{g}}_k$, controlled by the rational
  $R$-matrix $R(u) = 1 + r/u + O(u^{-2})$.
\item Both have generators in RTT form
  $T(u) = 1 + \sum_{r \geq 1} T^{(r)} u^{-r}$
  with quadratic relations
  $R_{12}(u{-}v)\,T_1(u)\,T_2(v) = T_2(v)\,T_1(u)\,R_{12}(u{-}v)$.
\item The Koszul dual of both is the $R^{-1}$-Yangian:
  replacing $R$ by $R^{-1}$ corresponds to
  $\hbar \mapsto -\hbar$.
\item Evaluation modules $V(a)$ and their tensor products
  behave identically in both constructions
  (Proposition~\ref{prop:eval-module-bar}).
\end{enumerate}
The constructions differ in their geometric origins:
$Y(\mathfrak{g})^{\mathrm{ch}}$ arises from FM configuration
space integrals on algebraic curves, while
$Y^{\mathrm{dg}}(\mathfrak{g})$ arises from line operators
in 3d holomorphic Chern--Simons theory~\textup{\cite{DNP25}}.
\end{proposition}

\begin{proof}
Part~(i) follows from comparing the deformation parameter:
both constructions deform the vertex algebra OPE by a
spectral parameter $u = z_1 - z_2$ that controls
$\Eone$-locality.  In the FM picture, $u$ is the
relative coordinate on $\overline{C}_2(X)$
(Theorem~\ref{thm:yangian-e1}).  In the DNP construction,
$u$ is the holomorphic coordinate along the topological
line (the ``spectral parameter'' of \cite[\S5]{DNP25}).

Part~(ii): the RTT presentation is a presentation of the
quadratic algebra, hence determined by the $R$-matrix.
Since both constructions use the same $R$-matrix, the
RTT relations agree.

Part~(iii) follows from Theorem~\ref{thm:yangian-koszul-dual}
(this manuscript) and \cite[Thm.~6.12]{DNP25}
(the Koszul dual of line operators is controlled by $R^{-1}$).

Part~(iv): the bar complex of the evaluation module
is the CE complex $C^*(\mathfrak{g}, V)$
(Proposition~\ref{prop:eval-module-bar}), which
depends only on the underlying $\mathfrak{g}$-action,
not on the geometric origin of the Yangian structure.
\end{proof}

(The complete identification of DNP's line-operator package with the bar-cobar twisting package is Theorem~\ref{thm:dnp-bar-cobar-identification} in Vol~II.)

\begin{remark}[Quasi-isomorphism question]
\label{rem:dg-shifted-qi}
The structural comparison above does not establish a
quasi-isomorphism $Y(\mathfrak{g})^{\mathrm{ch}}
\simeq Y^{\mathrm{dg}}(\mathfrak{g})$: this would require
constructing a separated complete RTT-level filtration on the
dg-shifted target whose finite quotients recover the theorematic finite
RTT stages.  Corollary~\ref{cor:yangian-hlevel-comparison-criterion}
shows that once such compatible finite quotients are in place, the
comparison with the coefficientwise RTT completion is formal.
Koszulness \ifannalsedition\else
(Remark~\ref{rem:yangian-collapse-conj})
\fi remains one natural
route to producing those compatible quotient identifications.
\end{remark}

\begin{remark}[Maurer--Cartan element as twisting morphism]
\label{rem:dnp-mc-twisting}
\index{Maurer--Cartan element!twisting morphism}
\index{Yang--Baxter equation!A-infinity@$A_\infty$}
The dg-shifted Yangian of \cite{DNP25} carries a
Maurer--Cartan element $r(z) \in \cA^! \otimes \cA^!$
satisfying an $A_\infty$ Yang--Baxter equation.
In the bar-cobar framework, this element admits a precise
identification: $r(z)$ is the \emph{twisting morphism}
$\tau\colon \bar{B}(\cA) \to \cA^!$
of Theorem~\ref{thm:bar-cobar-isomorphism-main},
restricted to the degree-$2$ component and evaluated at
spectral parameter~$z$.

Explicitly:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The MC equation $dr + r \star r = 0$ is the
  bar-cobar adjunction equation
  $\partial \tau + \tau \cup \tau = 0$,
  which is equivalent to $d_{\bar{B}}^2 = 0$
  (Theorem~\ref{thm:bar-nilpotency-complete}).
\item The $A_\infty$ Yang--Baxter equation of
  \cite[\S5]{DNP25} is the $\Eone$-chiral generalization:
  the bar complex differential encodes the RTT relation
  (Theorem~\ref{thm:yangian-bar-rtt}), and $d^2 = 0$
  is precisely the Yang--Baxter equation for $R(u)$.
\item The non-renormalization theorem of \cite[Thm.~4.1]{DNP25}
  (OPE of line operators is $1$-loop exact) corresponds to
  the Koszul property: the bar spectral sequence collapses
  at $E_2$, so the $A_\infty$ structure is determined by
  the quadratic ($R$-matrix) data.
\end{enumerate}

The bridge claim (Conjecture~\ref{conj:chiral-dg-shifted-qi}) is:
the $\Eone$-chiral Yangian and the dg-shifted Yangian are two
presentations of one object, one via configuration-space
integrals (this manuscript) and one via holomorphic
Chern--Simons perturbation theory~(\cite{DNP25}).  The missing
input is the Koszulness of the $\Eone$-chiral bar complex
\ifannalsedition\else
(Remark~\ref{rem:yangian-collapse-conj})
\fi.
\end{remark}

\begin{conjecture}[Chiral--dg-shifted quasi-isomorphism; \ClaimStatusConjectured]\label{conj:chiral-dg-shifted-qi}
The $\Eone$-chiral Yangian $Y(\fg)^{\mathrm{ch}}$ of this monograph and the
dg-shifted Yangian $Y^{\mathrm{dg}}(\fg)$ of Dimofte--Niu--Py~\cite{DNP25}
are quasi-isomorphic as $\Eone$-algebras.
\end{conjecture}

\begin{proposition}[Degree-2 mixed-tensor criterion for dg-shifted
local transport; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-degree2-mixed-tensor-criterion}
Let $\Ydg_{\cA}$ be a dg-shifted or factorization-theoretic Yangian
candidate with one-factor fundamental line operator
$L_a^{\mathrm{dg}}(u)\in \End(V)\otimes \End(V(a))$, $V=\mathbb{C}^M$,
and residue operator
$\Xi_a^{\mathrm{dg}}:=\operatorname*{Res}_{u=a}L_a^{\mathrm{dg}}(u)$.
Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the one-factor line operator is functorial for the diagonal
  $\mathfrak{sl}_M$-action and normalized by
  $L_a^{\mathrm{dg}}(u)\to 1$ as $u\to\infty$;
\item the local OPE on the fundamental line is one-loop exact, with
  simple pole computed by the degree-$2$ Maurer--Cartan element
  $r(z)=\tau|_{\deg 2}$ from Remark~\ref{rem:dnp-mc-twisting};
\item $\Xi_a^{\mathrm{dg}}(e_1\otimes e_2)=-\hbar(e_2\otimes e_1)$.
\end{enumerate}
Then $\Xi_a^{\mathrm{dg}}=-\hbar P$ and
$L_a^{\mathrm{dg}}(u)=R_{0a}(u-a)$.
If in addition the twisted-coproduct hypotheses of
Corollary~\ref{cor:dg-shifted-rtt-typea-single-line-bootstrap} hold on
universal packets and generic tensor powers, then the dg-shifted local
Yangian packet closes: every universal packet carries the standard
finite-stage evaluation action and $\Delta_{r,0}(N)=0$ for $0\le r\le N$
on the evaluation-generated core.

Equivalently, once the standard RTT side is fixed, the remaining local
transport problem is reduced to transporting the degree-$2$ twisting
coefficient on the ordered mixed-tensor line $e_1\otimes e_2$ to the
standard normalized residue.
\end{proposition}

\begin{proof}
Assumption~\textup{(iii)} is exactly the ordered mixed-tensor formula of
Proposition~\ref{prop:dg-shifted-rtt-typea-uniform-single-line}, while
\textup{(i)} supplies the functoriality and normalization hypotheses
used there and in
Corollary~\ref{cor:dg-shifted-rtt-typea-residue-reduction}, giving
$\Xi_a^{\mathrm{dg}}=-\hbar P$ and $L_a^{\mathrm{dg}}(u)=R_{0a}(u-a)$.
The twisted-coproduct statement follows verbatim from
Corollary~\ref{cor:dg-shifted-rtt-typea-single-line-bootstrap}.
\end{proof}

\begin{proposition}[Scalar normalization and Casimir reduction chain;
\ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-seed-normalized-coefficient}
\label{prop:dg-shifted-rtt-degree2-scalar-normalization}
\label{cor:dg-shifted-rtt-degree2-casimir-normalization}
\label{prop:dg-shifted-rtt-degree2-fundamental-casimir}
\label{cor:factorization-fundamental-casimir-identity}
\label{prop:dg-shifted-factorization-shared-seed}
\label{cor:yangian-typea-dg-local-closure}
In the setting of
Proposition~\ref{prop:dg-shifted-rtt-degree2-mixed-tensor-criterion}
with $M\ge2$, the following chain of reductions holds:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Seed-normalized extraction.}
  Writing the one-loop singular part in logarithmic normalization
  $r_a^{\mathrm{fund}}(z)\,\eta_{12}$, one has
  $\Xi_a^{\mathrm{dg}}=r_a^{\mathrm{fund}}(z)\big|_{z_1=z_2}$
  (since $\operatorname*{Res}_{z_1=z_2}\eta_{12}=1$
  by \eqref{eq:the-seed}), and the remaining local transport problem is
  $r_a^{\mathrm{fund}}(z)(e_1\otimes e_2)=-\hbar(e_2\otimes e_1)$.
\item \emph{Scalar normalization.}
  By $\mathfrak{sl}_M$-functoriality and Schur's lemma on
  $V\otimes V\cong\operatorname{Sym}^2(V)\oplus\Lambda^2(V)$,
  $\Xi_a^{(1)}=\alpha_a\,\id+\beta_a\,P$.  A scalar renormalization
  $L_a^{\mathrm{ren}}(u):=s_a(u)\,L_a^{\mathrm{dg}}(u)$ absorbs
  $\alpha_a$, leaving pure-permutation normalization
  $L_a^{\mathrm{ren}}(u)=1+\hbar\beta_a P/(u-a)+O(\hbar^2)$ with
  remaining input $\beta_a=-1$.
\item \emph{Casimir convention.}
  In the trace-zero convention
  $\Xi_a^{(1)}=\lambda_a(P-\frac{1}{M}\id)$, one has
  $\beta_a=\lambda_a$.  Inserting the fundamental Casimir
  $\Omega_{\mathfrak{sl}_M}^{\mathrm{fund}}=P-\frac{1}{M}\id$
  (using $\Omega_{\mathfrak{gl}_M}^{\mathrm{fund}}
  =\sum_{i,j}E_{ij}\otimes E_{ji}=P$) confirms
  $\lambda_a=\beta_a=-1$ and
  $r_{a,\mathrm{ren}}^{\mathrm{fund}}(z)(e_1\otimes e_2)
  =-\hbar(e_2\otimes e_1)$.
\item \emph{Factorization closure.}
  On the factorization side,
  $L_a^{\mathrm{std}}(u)=1-\hbar P/(u-a)$
  (Theorem~\ref{thm:yangian-e1},
  Proposition~\ref{prop:dg-shifted-rtt-standard-typea-local-packet})
  gives $\beta_a=-1$ immediately.
\item \emph{Shared bar seed.}
  If the dg-shifted and factorization degree-$2$ coefficients are both
  induced by $r(z)=\tau|_{\deg 2}$
  (Remark~\ref{rem:dnp-mc-twisting}), the shared seed forces
  $r_{a,\mathrm{dg}}^{\mathrm{fund}}
  =r_{a,\mathrm{fact}}^{\mathrm{fund}}
  =-\hbar(P-\frac{1}{M}\id)\big|_{z_1=z_2}$, giving $\beta_a=-1$ and
  $r_{a,\mathrm{dg,ren}}^{\mathrm{fund}}(z)(e_1\otimes e_2)
  =-\hbar(e_2\otimes e_1)$.
\item \emph{MC4 closure.}
  Under the shared bar seed, item~\textup{(a)} of
  Corollary~\ref{cor:yangian-typea-degree2-plus-generators} is
  automatic; the remaining MC4 input is compact generation plus
  transport on the completed fundamental evaluation packet, exactly as
  in Corollary~\ref{cor:yangian-typea-degree2-plus-generators}.
\end{enumerate}
\end{proposition}

\begin{proof}
Step~\textup{(i)}: the residue acts on the scalar factor only.
Steps~\textup{(ii)}-\textup{(iii)}: Schur's lemma and the Casimir
identity.
Step~\textup{(iv)}: direct from the standard line operator.
Step~\textup{(v)}: shared seed forces equality; factorization side
gives~$\beta_a=-1$.
Step~\textup{(vi)}: immediate from~\textup{(v)}.
\end{proof}

\begin{conjecture}[Finite-RTT quotient package on a dg model of the
canonical Yangian H-level target;
\ClaimStatusConjectured]
\label{conj:dg-shifted-yangian-rtt-package}
Let $\cA=\mathcal{Y}(\mathfrak{sl}_M)$,
$\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA}$
(Proposition~\ref{prop:yangian-canonical-hlevel-target}), and
$U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$
(Proposition~\ref{prop:yangian-canonical-envelope}).  There exists a
separated complete dg algebra $\Ydg_{\cA}$ (pole-order filtration),
quasi-isomorphic to $U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ and
admitting an RTT-adapted filtration
(Definition~\ref{def:rtt-adapted-filtration}): the filtration is
separated and complete for RTT level;
$\Ydg_{\cA}/F^{N+1}\Ydg_{\cA}$ records exactly the modes up to level
$N$; those quotients are dg quasi-isomorphic to $Y_{\le N}$; and the
comparison is compatible with evaluation modules and
$r(z)=\tau|_{\deg 2}$.  Assuming this,
Corollary~\ref{cor:yangian-hlevel-comparison-criterion} identifies
$\Ydg_{\cA}$ with $\widehat Y_{\mathrm{RTT}}$.
\end{conjecture}

\begin{remark}[Why line operators should control the filtration]
\label{rem:dg-shifted-filtration-evidence}
The canonical H-level target already exists (Proposition~\ref{prop:yangian-canonical-hlevel-target}); the remaining MC4 problem is to equip it with compatible RTT-level quotients.  Line-operator OPEs are organized by pole order, matching the RTT filtration, and the Maurer--Cartan element $r(z)$ appears as the degree-$2$ bar twisting morphism.
\end{remark}

\begin{remark}[First attack route for dg-shifted RTT quotients]
\label{rem:dg-shifted-quotient-route}
Conjecture~\ref{conj:dg-shifted-yangian-rtt-package} reduces to four stagewise checks: (i)~RTT-level ideals are preserved by the differential and coproduct; (ii)~the level-$N$ quotient depends only on the first $N$ OPE modes; (iii)~that quotient is identified with $Y_{\le N}$ via $R$-matrix relations; (iv)~the induced degree-$2$ twisting morphism matches $\tau|_{\deg 2}$.

The reduction chain then contracts: locality criterion (Proposition~\ref{prop:dg-shifted-rtt-locality-criterion}) $\to$ kernel coefficient criterion (Proposition~\ref{prop:dg-shifted-rtt-kernel-coefficient-criterion}) $\to$ evaluation detection (Proposition~\ref{prop:dg-shifted-rtt-evaluation-detection}) $\to$ boundary seed (Proposition~\ref{prop:dg-shifted-rtt-boundary-seed}) $\to$ fundamental propagation (Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation}) $\to$ auxiliary kernel identification.  For type~$A$, the entire chain collapses to a single ordered mixed-tensor check $\Xi_a(e_1\otimes e_2)=-\hbar(e_2\otimes e_1)$ (Corollary~\ref{cor:dg-shifted-rtt-typea-single-line}), which after scalar normalization reduces to the Casimir identity (Proposition~\ref{prop:dg-shifted-rtt-degree2-fundamental-casimir}).  This identity already holds on the factorization target (Corollary~\ref{cor:factorization-fundamental-casimir-identity}), so the remaining problem is the H-level realization of the dg-shifted target with compact generators.
\end{remark}

The following chain of propositions establishes successively weaker
sufficient conditions for identifying $Q_N:=\Ydg_{\cA}/F^{N+1}\Ydg_{\cA}$
with $Y_{\le N}$.  Each implies the preceding one; the proofs are
direct verifications of the preceding step's hypotheses.

\begin{proposition}[Stepwise reduction to evaluation detection;
\ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-presentation-criterion}
\label{prop:dg-shifted-rtt-locality-criterion}
\label{prop:dg-shifted-rtt-formula-preservation}
\label{prop:dg-shifted-rtt-coefficient-criterion}
\label{prop:dg-shifted-rtt-kernel-coefficient-criterion}
\label{prop:dg-shifted-rtt-oneloop-kernel-criterion}
\label{prop:dg-shifted-rtt-evaluation-detection}
The following conditions on the quotient
$Q_N:=\Ydg_{\cA}/F^{N+1}\Ydg_{\cA}$ are each sufficient for
$Q_N \cong Y_{\le N}$, listed from strongest to weakest.
Each step implies its predecessor by direct verification.
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Presentation level.}
  $Q_N$ is generated by $T_{ij}^{(r)}$ with $r \le N$ satisfying the
  truncated RTT relations and no further; evaluation modules agree with
  the finite RTT stage.  Then $Q_N\cong Y_{\le N}$ by the universal
  property of the truncated RTT presentation.

\item \emph{Pole-order locality.}
  The structure formulas are RTT-triangular: every term in
  $d(T_{ij}^{(r)})$, $\partial(T_{ij}^{(r)})$, the MC twisting, and
  $\Delta^{\mathrm{tw}}(T_{ij}^{(r)})$ contains a factor $T_{ab}^{(s)}$
  with $s \ge r$, and the level-$\ell$ part depends only on modes with
  $s \le \ell$.  Then $F^{N+1}\Ydg_{\cA}$ is preserved and $Q_N$ depends
  only on the first $N$ modes, reducing to~\textup{(i)}.

\item \emph{Rational line-operator formulas.}
  $T(z,u)=1+\hbar\sum_{r \ge 0} T^{(r)}(z)\,u^{-r-1}$; differential
  and translation act coefficientwise; MC correction from rational
  convolution; $\Delta^{\mathrm{tw}}T^{(\ell)}=\sum_{a+b=\ell}
  T^{(a)}\otimes T^{(b)}$.  Implies the locality hypotheses
  of~\textup{(ii)}.

\item \emph{Coefficient-level RTT.}
  The truncated monodromy matrix
  $T_N(u)=1+\hbar\sum_{0\le r\le N}T^{(r)}u^{-r-1}$ satisfies the
  standard truncated RTT relation in~$Q_N$; the $T^{(r)}_{ij}$ generate
  $Q_N$ with no further relations; evaluation modules match.
  Reduces to~\textup{(i)}.

\item \emph{Kernel-coefficient identity.}
  The OPE kernel coefficients
  $K_{a,b}=\operatorname{Coeff}_{u^{-a-1}v^{-b-1}}$ agree with the
  standard finite RTT coefficients and generate all relations.
  Reduces to~\textup{(iv)}.

\item \emph{One-loop kernel identity.}
  Define
  $\mathsf{K}^{\mathrm{line}}_{a,b}(N):=
  \operatorname{Coeff}_{u^{-a-1}v^{-b-1}}
  (R(u\!-\!v)\,T_{N,1}(u)\,T_{N,2}(v)
  -T_{N,2}(v)\,T_{N,1}(u)\,R(u\!-\!v))$
  and let $\mathsf{K}^{\mathrm{RTT}}_{a,b}(N)$ denote the standard
  coefficient.  If the OPE is one-loop exact and
  $\mathsf{K}^{\mathrm{line}}_{a,b}(N)
  =\mathsf{K}^{\mathrm{RTT}}_{a,b}(N)$ for all $a,b \le N$, then
  step~\textup{(v)} is satisfied.

\item \emph{Evaluation detection.}
  Let $\Delta_{a,b}(N):=
  \mathsf{K}^{\mathrm{line}}_{a,b}(N)
  -\mathsf{K}^{\mathrm{RTT}}_{a,b}(N)$.  If $Q_N$ is represented
  faithfully on tensor products of fundamental evaluation modules and
  $\Delta_{a,b}(N)$ acts by zero on that subcategory for all
  $a,b \le N$, then faithfulness forces $\Delta_{a,b}(N)=0$ and
  step~\textup{(vi)} is satisfied.
\end{enumerate}
\end{proposition}

\begin{proof}
Each step is verified by checking that the stated hypotheses imply
those of the preceding step.  Step~\textup{(i)} uses the universal
property; \textup{(ii)} uses RTT-triangularity to preserve ideals;
\textup{(iii)} verifies triangularity from the rational structure;
\textup{(iv)}-\textup{(vi)} match kernel coefficients with RTT
coefficients; \textup{(vii)} uses faithfulness of the evaluation
subcategory.
\end{proof}

\begin{remark}[Finite RTT stages as reduced-weight windows]
\label{rem:rtt-as-windows}
\index{reduced-weight window!Yangian identification}
The finite RTT stage $Q_N \cong Y_{\le N}$ is precisely the
reduced-weight-$N$ window $K_N(Y)$
(Definition~\ref{def:finite-window}) of the Yangian bar complex: the
pole-order locality of step~\textup{(ii)} means that the bar
differential on mode-degree $\le N$ involves only finitely many OPE
coefficients, and the arity cutoff
(Lemma~\ref{lem:arity-cutoff}) ensures these are determined by the
first $N$ modes.  For $\mathfrak{g}$-coloured towers with
$d = \dim\mathfrak{g}$, the window dimensions grow as
$\dim K_q(Y) = d(d+1)^{q-1}$
(\S\ref{sec:w-completion-kinematics}).  The coefficient-stability
criterion (Theorem~\ref{thm:coefficient-stability-criterion})
guarantees that once RTT coefficients stabilize on each window, the
completed bar-cobar round-trip is a quasi-isomorphism.  The jet
principle \ifannalsedition\else
(Conjecture~\ref{conj:jet-principle})
\fi then predicts that
the dg-shifted Yangian structure stabilizes through jet order~$q$.
\end{remark}

\begin{proposition}[Boundary-seed criterion for truncated RTT
defects; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-boundary-seed}
Fix $N \ge 0$ and let $\Delta_{a,b}(N)$ be the coefficient defect of
Proposition~\ref{prop:dg-shifted-rtt-evaluation-detection}.  If the
spectral recursion $\Delta_{a+1,b}(N)=\Delta_{a,b+1}(N)$ holds for
$a+b+1\le N$, the boundary defects $\Delta_{a,0}(N)$ act by zero on the
faithful evaluation family for $0\le a\le N$, and the evaluation action
is standard, then $\Delta_{a,b}(N)=0$ for $a+b\le N$, so
Proposition~\ref{prop:dg-shifted-rtt-evaluation-detection} is satisfied
after checking only $\{\Delta_{a,0}(N)\}_{0 \le a \le N}$.
\end{proposition}

\begin{proof}
The recursion gives $\Delta_{a,b}(N)=\Delta_{a+b,0}(N)$; faithfulness
and boundary vanishing force all defects to vanish.
\end{proof}

\begin{proposition}[Boundary-strip coefficient formula on the
evaluation packet; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-boundary-coefficient-formula}
Let $T_1(u)=\sum_{r\ge 0} T_1^{(r)}u^{-r}$,
$T_2(v)=\sum_{s\ge 0} T_2^{(s)}v^{-s}$ be the normalized fundamental
monodromy series, and expand
$R(u-v)=1-\hbar\sum_{t\ge 0} P_{12}\,u^{-t-1}v^t$ for $|u|>|v|$.
Then
\begin{multline*}
\operatorname{Coeff}_{u^{-a-1}v^{-1}}
\bigl(
R(u\!-\!v)\,T_1(u)\,T_2(v)-T_2(v)\,T_1(u)\,R(u\!-\!v)
\bigr)\\
=\;
T_1^{(a+1)}T_2^{(1)}-T_2^{(1)}T_1^{(a+1)}
-\hbar\!\sum_{t=0}^{a}\!
\bigl(
P_{12}\,T_1^{(a-t)}T_2^{(t+1)}
-T_2^{(t+1)}T_1^{(a-t)}P_{12}
\bigr).
\end{multline*}
\end{proposition}

\begin{proof}
Write $R^{(t)}=-\hbar P_{12}$.  The identity part of $R$ gives the
commutator term; matching $u$- and $v$-powers in the $R$-series forces
$T_1^{(a-t)}$ and $T_2^{(t+1)}$, and summing over $0\le t\le a$ yields
the result.
\end{proof}

\begin{proposition}[Explicit coefficient formula for the fundamental
monodromy series; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-fundamental-coefficient-formula}
Fix generic evaluation points $a_1,\dots,a_m$ and write
\[
T^{(m)}(u)=L_{a_1}(u)\cdots L_{a_m}(u)
=\sum_{r\ge0}T^{(m,r)}u^{-r},
\qquad
L_{a_j}(u)=1-\frac{\hbar P_{0j}}{u-a_j},
\]
on the tensor product
\[
M_m:=V_{\mathrm{fund}}(a_1)\otimes\cdots\otimes
V_{\mathrm{fund}}(a_m).
\]
Then
\[
T^{(m,0)}=1,
\]
and for every $r\ge1$ one has
\[
T^{(m,r)}
=
\sum_{s=1}^{\min(r,m)}(-\hbar)^s
\sum_{1\le j_1<\cdots<j_s\le m}
\sum_{\substack{n_1,\dots,n_s\ge0\\ n_1+\cdots+n_s=r-s}}
a_{j_1}^{n_1}\cdots a_{j_s}^{n_s}\,
P_{0j_1}\cdots P_{0j_s}.
\]
In particular, every summand of $T^{(m,r)}$ is supported on at most
$r$ quantum slots.
\end{proposition}

\begin{proof}
For each factor one has the geometric-series expansion
\[
L_{a_j}(u)
=
1-\hbar\sum_{n\ge0}a_j^n u^{-n-1}P_{0j}
\]
in the standard region $|u|>|a_j|$.  Multiplying the $m$ factors in the
fixed order $j=1,\dots,m$, the coefficient of $u^{-r}$ is obtained by
choosing the non-identity term from exactly $s$ factors
$j_1<\cdots<j_s$ and the identity term from the rest.  If the chosen
terms have degrees $n_1+1,\dots,n_s+1$, then the total $u$-degree
condition is
\[
(n_1+1)+\cdots+(n_s+1)=r,
\]
equivalently $n_1+\cdots+n_s=r-s$.  The contribution of that choice is
\[
(-\hbar)^s a_{j_1}^{n_1}\cdots a_{j_s}^{n_s}
P_{0j_1}\cdots P_{0j_s},
\]
and summing over all subsets and all nonnegative tuples
$(n_1,\dots,n_s)$ gives the displayed formula.

The final sentence is immediate: a summand with $s$ chosen factors
acts nontrivially only on the corresponding $s$ quantum slots, and
$s\le r$.
\end{proof}

\begin{proposition}[Support bound and finite detection for boundary-strip
RTT defects; \ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-boundary-support-bound}
\label{prop:dg-shifted-rtt-defect-support-mechanism}
\label{prop:dg-shifted-rtt-universal-generic-packets}
\label{cor:dg-shifted-rtt-minimal-canonical-family}
\label{prop:dg-shifted-rtt-finite-tensor-detection}
Fix $N \ge 0$ and let
$\Delta_{a,0}(N)
=\mathsf{K}^{\mathrm{line}}_{a,0}(N)
-\mathsf{K}^{\mathrm{RTT}}_{a,0}(N)$
be the boundary-strip defect family from
Proposition~\ref{prop:dg-shifted-rtt-boundary-seed}.
The following chain of reductions holds:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Support bound.}
  Every summand of $\mathsf{K}^{\mathrm{line},(m)}_{a,0}$ and of the
  defect $\Delta_{a,0}(N)$ (when homogeneous of RTT degree $a+1$) is
  supported on at most $a+1$ quantum slots.  On the line side this
  follows from
  Propositions~\ref{prop:dg-shifted-rtt-boundary-coefficient-formula}
  and~\ref{prop:dg-shifted-rtt-fundamental-coefficient-formula}: in the
  commutator, summands on disjoint slots cancel, and in the series
  each summand satisfies $(a-t)+(t+1)=a+1$.  On the defect side, the
  coefficientwise coproduct forces the same bound.
\item \emph{Universal generic packet.}
  For algebraically independent parameters $x_1,\dots,x_m$ and
  $M_m^{\mathrm{gen}}
  :=V_{\mathrm{fund}}(x_1)\otimes\cdots\otimes V_{\mathrm{fund}}(x_m)$,
  the matrix entries of $\Delta^{(m)}_{a,0}(N)$ lie in
  $\mathbb{C}[x_1,\dots,x_m]$.  Therefore $\Delta_{a,0}(N)$ vanishes
  on all generic tensor products of length $m$ if and only if it
  vanishes on the single universal packet $M_m^{\mathrm{gen}}$.
\item \emph{Minimal canonical family.}
  Combining~\textup{(i)} and~\textup{(ii)}, to prove
  $\Delta_{a,0}(N)=0$ it is enough to verify vanishing on the
  canonical packets $M_m^{\mathrm{gen}}$ for $1\le m\le a+1$.
\item \emph{Finite tensor-length detection.}
  Assume the defect is homogeneous of RTT degree $a+1$, the
  coefficientwise coproduct law holds, evaluation modules are standard,
  the faithful evaluation subcategory is generated by generic tensor
  products, and $\Delta_{a,0}(N)$ acts by zero on each canonical
  universal packet $M_m^{\mathrm{gen}}$ for $1\le m\le a+1$.  Then
  $\Delta_{a,0}(N)=0$ for all $0 \le a \le N$: the minimal family
  from~\textup{(iii)} kills all generic tensor products, and the
  generation hypothesis propagates to the whole faithful subcategory.
\end{enumerate}
\end{proposition}

\begin{proof}
Step~\textup{(i)}: the line-side bound follows from the explicit
coefficient formula
(Proposition~\ref{prop:dg-shifted-rtt-fundamental-coefficient-formula})
and the boundary-strip formula
(Proposition~\ref{prop:dg-shifted-rtt-boundary-coefficient-formula});
the defect-side bound follows from RTT degree homogeneity and the
coproduct structure.
Step~\textup{(ii)}: polynomial dependence on evaluation parameters
follows from the explicit coefficient formula; vanishing on an open
subset forces vanishing of the polynomial.
Steps~\textup{(iii)}-\textup{(iv)}: combine the support bound, the
universal-packet reduction, and the faithful-subcategory generation
hypothesis.
\end{proof}

\begin{proposition}[Top-packet induction and closure; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-top-packet-induction}
\label{prop:dg-shifted-rtt-top-packet-line-formula}
\label{cor:dg-shifted-rtt-top-packet-comparison}
\label{prop:dg-shifted-rtt-top-packet-standard-discharge}
\label{cor:dg-shifted-rtt-top-packet-conditional-closure}
\label{prop:dg-shifted-rtt-universal-evaluation-rigidity}
\label{cor:dg-shifted-rtt-top-packet-from-one-factor}
Set $m:=a+1$ and let $M_m^{\mathrm{gen}}$ be the top universal packet.
Let $\mathsf{F}_{<m}\End(V^{\otimes 2}\otimes M_m^{\mathrm{gen}})$ be
the span of operators supported on proper subsets of $[m]$.
The following chain of results holds:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Top-packet reduction.}
  Once the shorter universal packets $M_r^{\mathrm{gen}}$ ($r\le a$)
  are killed, $\Delta^{(m)}_{a,0}(N)=0$ if and only if its class in
  $\End(V^{\otimes 2}\otimes M_m^{\mathrm{gen}})/\mathsf{F}_{<m}$
  vanishes (proper-support summands factor through killed packets).
\item \emph{Line-side top-support formula.}
  The image of $\mathsf{K}^{\mathrm{line},(m)}_{a,0}$ in the quotient
  is the parameter-free operator
  \[
  \Omega_a^{\mathrm{line}}
  :=
  (-\hbar)^{a+2}
  \biggl[
  \sum_{j=1}^{m}
  \bigl(P_{\alpha,[m]}P_{\beta,j}-P_{\beta,j}P_{\alpha,[m]}\bigr)
  +\!\!\sum_{S\subsetneq [m]}\!\!
  \bigl(P_{\alpha\beta}P_{\alpha,S}P_{\beta,S^c}
  -P_{\beta,S^c}P_{\alpha,S}P_{\alpha\beta}\bigr)
  \biggr],
  \]
  where $P_{\alpha,S}:=P_{\alpha s_1}\cdots P_{\alpha s_r}$ for
  $S=\{s_1<\cdots<s_r\}$.  This follows from the full-support extraction:
  $T_\alpha^{(m)}\equiv(-\hbar)^m P_{\alpha,[m]}$ and
  $T_\beta^{(1)}=-\hbar\sum_j P_{\beta,j}$ modulo $\mathsf{F}_{<m}$.
\item \emph{Top-packet comparison.}
  The defect class is
  $[\Delta^{(a+1)}_{a,0}(N)]
  =\Omega_a^{\mathrm{line}}-\Omega_a^{\mathrm{RTT}}(N)$,
  so the induction closes if and only if
  $\Omega_a^{\mathrm{RTT}}(N)=\Omega_a^{\mathrm{line}}$.
\item \emph{Standard-evaluation discharge.}
  Under the standard evaluation realization
  $T_N^{\mathrm{std}}(u)=L_{x_1}(u)\cdots L_{x_m}(u)$, the exact RTT
  relation forces the coefficient of $u^{-a-1}v^{-1}$ to act by zero;
  the support extraction then gives
  $\Omega_a^{\mathrm{RTT}}(N)=\Omega_a^{\mathrm{line}}=0$.
\item \emph{Conditional closure.}
  If the truncated quotient acts on $M_{a+1}^{\mathrm{gen}}$ by the
  standard evaluation action, the top-packet induction step closes
  by~\textup{(iv)}.
\item \emph{Evaluation rigidity.}
  If the one-factor packet $M_1^{\mathrm{gen}}=V_{\mathrm{fund}}(x)$
  carries the standard auxiliary kernel
  $L_x(u)=R_{0x}(u-x)=1-\hbar P_{0x}/(u-x)$ and tensor powers are
  governed by the coefficientwise coproduct law
  $T_N^{(m+1)}(u)=T_N^{(m)}(u)\,L_{x_{m+1}}(u)$, then
  $T_N^{(m)}(u)=L_{x_1}(u)\cdots L_{x_m}(u)$ for all $m\ge1$
  (induction on~$m$).
\item \emph{One-factor closure.}
  Under the hypotheses of~\textup{(vi)}, the top-packet induction step
  closes.  The only remaining Yangian task on the universal-packet side
  is to transport the one-factor line operator to $L_x(u)=R_{0x}(u-x)$.
\end{enumerate}
\end{proposition}

\begin{proof}
Step~\textup{(i)}: proper-support summands factor through shorter
packets (Proposition~\ref{prop:dg-shifted-rtt-defect-support-mechanism}).
Step~\textup{(ii)}: modulo $\mathsf{F}_{<m}$, only full-support terms
survive in
Proposition~\ref{prop:dg-shifted-rtt-boundary-coefficient-formula};
the explicit coefficient formula
(Proposition~\ref{prop:dg-shifted-rtt-fundamental-coefficient-formula})
gives the displayed result.
Step~\textup{(iii)}: definition of the defect class.
Step~\textup{(iv)}: the exact RTT relation on the standard evaluation
realization forces the coefficient to vanish; the same support extraction
gives $\Omega_a^{\mathrm{line}}=0$ in the quotient.
Steps~\textup{(v)}-\textup{(vii)}: combine the preceding steps with
the induction on tensor factors.
\end{proof}

\begin{proposition}[Fundamental propagation criterion for boundary-strip
RTT defects; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-fundamental-propagation}
Fix $N \ge 0$, and for generic evaluation points
$a_1,\dots,a_m$ write
\[
M_m:=V_{\mathrm{fund}}(a_1)\otimes\cdots\otimes V_{\mathrm{fund}}(a_m).
\]
Let
\[
\mathcal{D}_N(u,v):=
R(u-v)\,T_{N,1}(u)\,T_{N,2}(v)
-T_{N,2}(v)\,T_{N,1}(u)\,R(u-v)
\]
be the truncated RTT defect operator whose coefficients are the
boundary-strip defects of
Proposition~\ref{prop:dg-shifted-rtt-boundary-seed}.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item on every generic tensor power $M_m$, the truncated monodromy
  matrix is obtained by iterating the twisted coproduct, so that
  \[
  T_N^{(m+1)}(u)=T_N^{(m)}(u)\,L_{m+1}(u)
  \]
  with $L_{m+1}(u)$ the one-factor fundamental monodromy matrix acting
  on the last tensor factor, and operators supported on disjoint
  quantum slots commute;
\item for every generic fundamental evaluation module
  $V_{\mathrm{fund}}(a)$, the one-factor monodromy matrix $L(u)$
  satisfies the standard truncated RTT relation, equivalently
  \[
  \mathcal{D}_N(u,v)\big|_{V_{\mathrm{fund}}(a)}=0;
  \]
\item the faithful evaluation subcategory of
  Proposition~\ref{prop:dg-shifted-rtt-evaluation-detection} is
  generated from the generic tensor powers $M_m$ by finite direct sums
  and subquotients; and
\item the standard evaluation action of $T_N(u)$ is compatible with the
  same twisted-coproduct multiplication law.
\end{enumerate}
Then $\mathcal{D}_N(u,v)$ acts by zero on every object of the faithful
evaluation subcategory.  Consequently
\[
\Delta_{a,0}(N)=0
\qquad (0\le a\le N),
\]
so
Propositions~\ref{prop:dg-shifted-rtt-boundary-seed}
and~\ref{prop:dg-shifted-rtt-evaluation-detection}
identify the quotient with $Y_{\le N}$ once the degree-$2$ twisting
morphism matches $\tau|_{\deg 2}$.
\end{proposition}

\begin{proof}
We first show by induction on $m$ that
\[
\mathcal{D}_N(u,v)\big|_{M_m}=0
\qquad\text{for every } m\ge 1.
\]
For $m=1$ this is assumption~\textup{(ii)}.

Assume the statement for $M_m$.  By assumption~\textup{(i)}, on
$M_{m+1}=M_m\otimes V_{\mathrm{fund}}(a_{m+1})$ one has
\[
T_N^{(m+1)}(u)=T_N^{(m)}(u)\,L_{m+1}(u),
\qquad
T_N^{(m+1)}(v)=T_N^{(m)}(v)\,L_{m+1}(v).
\]
Since the last tensor factor commutes with the earlier quantum slots,
we compute
\begin{align*}
R\,T^{(m+1)}_{N,1}(u)\,T^{(m+1)}_{N,2}(v)
&=
R\,T^{(m)}_{N,1}(u)\,T^{(m)}_{N,2}(v)\,
L_{m+1,1}(u)\,L_{m+1,2}(v) \\
&=
T^{(m)}_{N,2}(v)\,T^{(m)}_{N,1}(u)\,
R\,L_{m+1,1}(u)\,L_{m+1,2}(v) \\
&=
T^{(m)}_{N,2}(v)\,T^{(m)}_{N,1}(u)\,
L_{m+1,2}(v)\,L_{m+1,1}(u)\,R \\
&=
T^{(m+1)}_{N,2}(v)\,T^{(m+1)}_{N,1}(u)\,R.
\end{align*}
The second equality uses the induction hypothesis on $M_m$, and the
third uses the one-factor RTT relation from assumption~\textup{(ii)} on
the last tensor factor.  Hence the defect vanishes on $M_{m+1}$.

By assumption~\textup{(iii)}, every object of the faithful evaluation
subcategory is built from the generic tensor powers $M_m$ by finite
direct sums and subquotients.  Vanishing of the defect operator is
preserved under those operations, so $\mathcal{D}_N(u,v)$ acts by zero
on the whole faithful evaluation subcategory.  Assumption~\textup{(iv)}
supplies the standard evaluation compatibility required by
Proposition~\ref{prop:dg-shifted-rtt-evaluation-detection}, which then
forces all boundary-strip coefficients $\Delta_{a,0}(N)$ to vanish.
\end{proof}

\begin{proposition}[Auxiliary-kernel criterion for fundamental RTT
propagation; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-auxiliary-kernel-criterion}
Fix $N \ge 0$ and let $R(u)$ be the rational Yang $R$-matrix on
$V_{\mathrm{fund}}\otimes V_{\mathrm{fund}}$, satisfying the
Yang--Baxter equation
\[
R_{12}(u-v)\,R_{13}(u-a)\,R_{23}(v-a)
=
R_{23}(v-a)\,R_{13}(u-a)\,R_{12}(u-v).
\]
Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item for every generic evaluation point $a$, the one-factor
  fundamental monodromy matrix induced by the line operator is the
  truncated auxiliary kernel
  \[
  L_a(u)=R_{0a}(u-a)
  \]
  on the fundamental evaluation module
  $V_{\mathrm{fund}}(a)$;
\item on generic tensor products of fundamental evaluation modules, the
  truncated monodromy matrix is obtained by the same twisted-coproduct
  multiplication law used in
  Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation}.
\end{enumerate}
Then the fundamental one-factor matrices satisfy the truncated RTT
relation
\[
R_{12}(u-v)\,L_{1,a}(u)\,L_{2,a}(v)
=
L_{2,a}(v)\,L_{1,a}(u)\,R_{12}(u-v)
\]
on every fundamental evaluation module.  Consequently the hypotheses of
Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation} are
satisfied, so the Yangian finite-detection problem reduces to the
single pairwise kernel identity
$L_a(u)=R_{0a}(u-a)$ on the fundamental line operator, together with
the standard twisted-coproduct multiplication law.
\end{proposition}

\begin{proof}
By assumption~\textup{(i)},
\[
L_{1,a}(u)=R_{1a}(u-a),
\qquad
L_{2,a}(v)=R_{2a}(v-a),
\]
where indices $1,2$ denote the two auxiliary copies of the fundamental
representation and $a$ denotes the quantum space
$V_{\mathrm{fund}}(a)$.  Substituting these expressions into the RTT
relation gives
\[
R_{12}(u-v)\,R_{1a}(u-a)\,R_{2a}(v-a)
=
R_{2a}(v-a)\,R_{1a}(u-a)\,R_{12}(u-v),
\]
which is exactly the Yang--Baxter equation for the rational Yang
$R$-matrix.  Therefore the one-factor fundamental monodromy satisfies
the RTT relation.

Assumptions~\textup{(i)} and~\textup{(ii)} are exactly the hypotheses of
Proposition~\ref{prop:dg-shifted-rtt-universal-evaluation-rigidity}, so
every universal packet carries the standard finite-stage evaluation
action.  In particular, the standard evaluation compatibility required
in Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation} is
automatic.  Hence that proposition applies and kills the entire
boundary strip.
\end{proof}

\begin{proposition}[Type-A uniqueness of the auxiliary kernel on the
fundamental line; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-typea-auxiliary-uniqueness}
Let $V=\mathbb{C}^M$ be the defining representation of
$\mathfrak{sl}_M$, and let
\[
L_a(u)\in \End(V)\otimes\End(V(a))
\]
be a rational one-factor monodromy matrix on the fundamental
evaluation module $V(a)$.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $L_a(u)$ is $\mathfrak{sl}_M$-equivariant on
  $V\otimes V(a)$;
\item $L_a(u)$ is regular away from $u=a$ and has unit asymptotic
  \[
  L_a(u)\to 1
  \qquad (u\to\infty);
  \]
\item the only pole is simple at $u=a$, with residue
  \[
  \operatorname*{Res}_{u=a}L_a(u)=-\hbar P,
  \]
  where $P$ is the permutation operator on
  $V\otimes V(a)\cong V\otimes V$.
\end{enumerate}
Then
\[
L_a(u)=1-\frac{\hbar P}{u-a}=R_{0a}(u-a),
\]
the standard rational Yang $R$-matrix on the defining fundamental
representation.  Consequently, for the standard type-A RTT tower the
pairwise problem of
Proposition~\ref{prop:dg-shifted-rtt-auxiliary-kernel-criterion}
reduces to these three local checks.
\end{proposition}

\begin{proof}
Because
\[
V\otimes V \cong \operatorname{Sym}^2(V)\oplus \Lambda^2(V),
\]
and both summands are irreducible $\mathfrak{sl}_M$-modules, every
$\mathfrak{sl}_M$-equivariant endomorphism of $V\otimes V$ acts by a
scalar on each summand.  Equivalently,
\[
L_a(u)=\alpha(u)\,1+\beta(u)\,P
\]
for rational scalar functions $\alpha(u),\beta(u)$.

The unit asymptotic implies
\[
\alpha(u)\to 1,\qquad \beta(u)\to 0
\qquad (u\to\infty).
\]
The residue condition says that the only pole is simple at $u=a$ and
its residue is exactly $-\hbar P$.  Hence $\alpha(u)$ has no pole and
must therefore be the constant function $1$, while $\beta(u)$ has the
unique form
\[
\beta(u)=-\frac{\hbar}{u-a}.
\]
Substituting these two functions gives
\[
L_a(u)=1-\frac{\hbar P}{u-a},
\]
which is precisely the standard rational Yang $R$-matrix kernel
$R_{0a}(u-a)$.
\end{proof}

\begin{corollary}[Type-A residue reduction for the auxiliary kernel;
\ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-typea-residue-reduction}
In the setting of
Proposition~\ref{prop:dg-shifted-rtt-typea-auxiliary-uniqueness},
assume further that the one-factor fundamental line operator is
constructed in a way that is functorial for the diagonal
$\mathfrak{sl}_M$-action on $V\otimes V(a)$ and normalized so that
widely separated lines have trivial transport:
\[
L_a(u)\to 1
\qquad (u\to\infty).
\]
Then to prove the pairwise auxiliary-space identity
\[
L_a(u)=R_{0a}(u-a)
\]
it is enough to verify the single local residue formula
\[
\operatorname*{Res}_{u=a}L_a(u)=-\hbar P.
\]

Equivalently, for the standard type-A RTT tower the genuinely analytic
Yangian problem on the fundamental line is the residue extraction at
the simple pole; the symmetry and asymptotic parts are formal once the
line operator is fixed.
\end{corollary}

\begin{proof}
The functoriality hypothesis gives the $\mathfrak{sl}_M$-equivariance
required in
Proposition~\ref{prop:dg-shifted-rtt-typea-auxiliary-uniqueness}, and
the normalization hypothesis gives the required unit asymptotic.  Hence
that proposition applies as soon as the displayed residue identity is
verified.  The final sentence is just a restatement of this reduction.
\end{proof}

\begin{proposition}[Type-A residue detection on the symmetric and
antisymmetric channels; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-typea-residue-channels}
In the setting of
Proposition~\ref{prop:dg-shifted-rtt-typea-auxiliary-uniqueness}, let
\[
\Xi_a:=\operatorname*{Res}_{u=a}L_a(u)\in \End(V\otimes V(a)).
\]
Then the residue identity
\[
\Xi_a=-\hbar P
\]
holds if and only if $\Xi_a$ acts by the scalar $-\hbar$ on the
symmetric summand $\operatorname{Sym}^2(V)$ and by the scalar $+\hbar$ on the
antisymmetric summand $\Lambda^2(V)$.

Equivalently, after identifying $V(a)\cong V$, it is enough to check
the two highest-weight channel formulas
\[
\Xi_a(e_1\otimes e_1)=-\hbar(e_1\otimes e_1),
\qquad
\Xi_a(e_1\otimes e_2-e_2\otimes e_1)
=+\hbar(e_1\otimes e_2-e_2\otimes e_1).
\]
Consequently, for the standard type-A RTT tower the remaining analytic
Yangian problem on the fundamental line is a two-channel scalar
residue computation.
\end{proposition}

\begin{proof}
By the $\mathfrak{sl}_M$-equivariance hypothesis of
Proposition~\ref{prop:dg-shifted-rtt-typea-auxiliary-uniqueness}, the
operator $\Xi_a$ preserves the irreducible decomposition
\[
V\otimes V \cong \operatorname{Sym}^2(V)\oplus \Lambda^2(V).
\]
Schur's lemma therefore gives scalars $\lambda_{\mathrm{sym}}$ and
$\lambda_{\mathrm{alt}}$ such that
\[
\Xi_a\big|_{\operatorname{Sym}^2(V)}=\lambda_{\mathrm{sym}}\id,
\qquad
\Xi_a\big|_{\Lambda^2(V)}=\lambda_{\mathrm{alt}}\id.
\]
The permutation operator acts by $+1$ on $\operatorname{Sym}^2(V)$ and by $-1$ on
$\Lambda^2(V)$.  Hence $\Xi_a=-\hbar P$ is equivalent to the two scalar
equalities
\[
\lambda_{\mathrm{sym}}=-\hbar,
\qquad
\lambda_{\mathrm{alt}}=+\hbar.
\]
The displayed highest-weight vectors generate the two irreducible
summands, so checking the action there is equivalent to checking the two
channel scalars themselves.
\end{proof}

\begin{corollary}[Type-A residue detection on one mixed tensor line;
\ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-typea-single-line}
Assume the hypotheses of
Proposition~\ref{prop:dg-shifted-rtt-typea-residue-channels}, and
assume $M\ge 2$.  Then the residue identity
\[
\Xi_a=-\hbar P
\]
is equivalent to the single mixed-tensor formula
\[
\Xi_a(e_1\otimes e_2)=-\hbar(e_2\otimes e_1).
\]

Equivalently, for the standard type-A RTT tower the remaining analytic
Yangian problem on the fundamental line may be checked on one ordered
off-diagonal tensor line.
\end{corollary}

\begin{proof}
Write
\[
s:=e_1\otimes e_2+e_2\otimes e_1\in \operatorname{Sym}^2(V),
\qquad
a:=e_1\otimes e_2-e_2\otimes e_1\in \Lambda^2(V),
\]
so that
\[
e_1\otimes e_2=\frac{1}{2}(s+a).
\]
If $\Xi_a=-\hbar P$, then the displayed formula is immediate.

Conversely, by
Proposition~\ref{prop:dg-shifted-rtt-typea-residue-channels}, the
operator $\Xi_a$ acts by scalars
$\lambda_{\mathrm{sym}},\lambda_{\mathrm{alt}}$ on
$\operatorname{Sym}^2(V)$ and $\Lambda^2(V)$, so
\[
\Xi_a(e_1\otimes e_2)
=\frac{1}{2}\lambda_{\mathrm{sym}}\,s
+\frac{1}{2}\lambda_{\mathrm{alt}}\,a
=\frac{\lambda_{\mathrm{sym}}+\lambda_{\mathrm{alt}}}{2}\,
e_1\otimes e_2
+\frac{\lambda_{\mathrm{sym}}-\lambda_{\mathrm{alt}}}{2}\,
e_2\otimes e_1.
\]
If this equals $-\hbar(e_2\otimes e_1)$, then comparing the
coefficients of the linearly independent tensors
$e_1\otimes e_2$ and $e_2\otimes e_1$ gives
\[
\lambda_{\mathrm{sym}}+\lambda_{\mathrm{alt}}=0,
\qquad
\lambda_{\mathrm{sym}}-\lambda_{\mathrm{alt}}=-2\hbar.
\]
Hence $\lambda_{\mathrm{sym}}=-\hbar$ and
$\lambda_{\mathrm{alt}}=+\hbar$, so
Proposition~\ref{prop:dg-shifted-rtt-typea-residue-channels} yields
$\Xi_a=-\hbar P$.
\end{proof}

\begin{proposition}[Uniform residue extraction from one ordered tensor
line; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-typea-uniform-single-line}
Assume the hypotheses of
Corollary~\ref{cor:dg-shifted-rtt-typea-residue-reduction}, and assume
$M\ge2$.  If the one-factor residue operator extracted from the
fundamental line operator satisfies
\[
\Xi_a(e_1\otimes e_2)=-\hbar(e_2\otimes e_1),
\]
then in fact
\[
\Xi_a(e_i\otimes e_j)=-\hbar(e_j\otimes e_i)
\qquad (1\le i,j\le M).
\]
Equivalently,
\[
\Xi_a=-\hbar P
\]
on all of $V\otimes V(a)\cong V\otimes V$.

Thus the mixed-tensor residue packet is uniform in the rank: once it is
proved on one ordered off-diagonal tensor line, the entire residue of
the one-factor line operator is determined.
\end{proposition}

\begin{proof}
By the functoriality hypothesis in
Corollary~\ref{cor:dg-shifted-rtt-typea-residue-reduction}, the
operator $\Xi_a$ is $\mathfrak{sl}_M$-equivariant.  Therefore, as in the
proof of
Proposition~\ref{prop:dg-shifted-rtt-typea-auxiliary-uniqueness},
Schur's lemma for
\[
V\otimes V\cong \operatorname{Sym}^2(V)\oplus \Lambda^2(V)
\]
shows that
\[
\Xi_a=\alpha\,\id+\beta\,P
\]
for scalars $\alpha,\beta\in\mathbb{C}$.

Applying this formula to $e_1\otimes e_2$ gives
\[
\Xi_a(e_1\otimes e_2)
=
\alpha(e_1\otimes e_2)+\beta(e_2\otimes e_1).
\]
By hypothesis this equals $-\hbar(e_2\otimes e_1)$.  Since
$e_1\otimes e_2$ and $e_2\otimes e_1$ are linearly independent, one
must have
\[
\alpha=0,\qquad \beta=-\hbar.
\]
Hence $\Xi_a=-\hbar P$, and therefore for every $i,j$,
\[
\Xi_a(e_i\otimes e_j)=-\hbar P(e_i\otimes e_j)
=-\hbar(e_j\otimes e_i).
\]
\end{proof}

\begin{corollary}[Type-A single-line bootstrap to standard evaluation
and boundary-strip vanishing; \ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-typea-single-line-bootstrap}
Assume the hypotheses of
Corollary~\ref{cor:dg-shifted-rtt-typea-residue-reduction}
and
Corollary~\ref{cor:dg-shifted-rtt-typea-single-line}.  Assume
further:
\begin{enumerate}[label=\textup{(\roman*)}]
\item on every universal packet, the truncated monodromy matrices are
  obtained by iterating the coefficientwise twisted-coproduct
  multiplication law of
  Proposition~\ref{prop:dg-shifted-rtt-universal-evaluation-rigidity};
\item on generic tensor powers of fundamental evaluation modules, the
  truncated monodromy matrix is obtained by the twisted-coproduct
  multiplication law of
  Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation};
\item the faithful evaluation subcategory of
  Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation} is
  generated from those generic tensor powers by finite direct sums and
  subquotients.
\end{enumerate}
If
\[
\Xi_a(e_1\otimes e_2)=-\hbar(e_2\otimes e_1),
\]
then:
\begin{enumerate}[label=\textup{(\alph*)}]
\item the one-factor fundamental kernel is the standard auxiliary
  kernel
  \[
  L_a(u)=R_{0a}(u-a);
  \]
\item every universal packet $M_m^{\mathrm{gen}}$, and in particular
  the top packet of
  Proposition~\ref{prop:dg-shifted-rtt-top-packet-induction}, carries
  the standard finite-stage evaluation action;
\item the truncated RTT defect
  \[
  \mathcal{D}_N(u,v)
  =
  R(u-v)\,T_{N,1}(u)\,T_{N,2}(v)
  -
  T_{N,2}(v)\,T_{N,1}(u)\,R(u-v)
  \]
  acts by zero on the faithful evaluation subcategory, so
  \[
  \Delta_{r,0}(N)=0
  \qquad (0\le r\le N).
  \]
\end{enumerate}
Thus, for the standard type-A Yangian tower, the universal-packet
transport problem and the boundary-strip finite-detection packet both
close once the dg-shifted or factorization one-factor line operator is
shown to carry the standard normalized mixed-tensor residue on the
fundamental line, equivalently once the displayed mixed-tensor formula
is proved.
\end{corollary}

\begin{proof}
By
Proposition~\ref{prop:dg-shifted-rtt-typea-uniform-single-line},
the displayed mixed-tensor formula already forces
\[
\Xi_a=-\hbar P
\]
uniformly on $V\otimes V(a)$.  Corollary~\ref{cor:dg-shifted-rtt-typea-residue-reduction}
therefore gives the one-factor auxiliary-kernel identity
\[
L_a(u)=R_{0a}(u-a).
\]
This proves~\textup{(a)}.

Now apply
Proposition~\ref{prop:dg-shifted-rtt-universal-evaluation-rigidity}.
Its one-factor hypothesis has just been established, and
assumption~\textup{(i)} supplies the twisted-coproduct multiplication
law on universal packets.  Hence every universal packet carries the
standard finite-stage evaluation action, proving~\textup{(b)}.

Specializing the universal parameters gives the same standard
finite-stage evaluation action on every generic tensor power of
fundamental evaluation modules.  Using assumption~\textup{(ii)},
Proposition~\ref{prop:dg-shifted-rtt-auxiliary-kernel-criterion}
shows that the one-factor monodromy satisfies the truncated RTT
relation on every fundamental evaluation module.  Therefore the only
remaining hypotheses of
Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation}
are exactly assumptions~\textup{(ii)} and~\textup{(iii)} above, and
that proposition implies that
\[
\mathcal{D}_N(u,v)
\]
acts by zero on the faithful evaluation subcategory.  Its coefficients
are precisely the boundary-strip defects
$\Delta_{r,0}(N)$, so those defects vanish for all $0\le r\le N$.
This is~\textup{(c)}.
\end{proof}

\begin{proposition}[Standard type-A fundamental line operator has the
standard local residue; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-standard-typea-local-packet}
Work in the theorematic standard type-A RTT tower, let
$V=\mathbb{C}^M$ be the defining representation, and let $V(a)$ be the
fundamental evaluation module at spectral parameter~$a$.  Let
$L_a^{\mathrm{std}}(u)$ be the normalized one-factor monodromy kernel
obtained by specializing the $R$-matrix-valued simple-pole OPE of
Theorem~\ref{thm:yangian-e1} to the defining evaluation module via
\eqref{eq:yangian-r-matrix}.  Then
\[
L_a^{\mathrm{std}}(u)=R_{0a}(u-a)=1-\frac{\hbar P}{u-a}.
\]
Hence
\[
\Xi_a^{\mathrm{std}}
:=
\operatorname*{Res}_{u=a}L_a^{\mathrm{std}}(u)
=-\hbar P,
\]
so for every $1\le i,j\le M$ one has
\[
\Xi_a^{\mathrm{std}}(e_i\otimes e_j)=-\hbar(e_j\otimes e_i).
\]
In particular,
\[
\Xi_a^{\mathrm{std}}(e_1\otimes e_2)=-\hbar(e_2\otimes e_1).
\]
\end{proposition}

\begin{proof}
Theorem~\ref{thm:yangian-e1} identifies the one-factor OPE kernel with
the rational Yang $R$-matrix, and
\eqref{eq:yangian-r-matrix} specializes that kernel to the evaluation
module at spectral parameter~$a$.  On the standard type-A defining
representation, the rational Yang $R$-matrix is
\[
R(u)=1-\frac{\hbar P}{u}
\]
by Remark~\ref{rem:rational-trigonometric-dk}.  Shifting the additive
spectral parameter by~$a$ gives
\[
L_a^{\mathrm{std}}(u)=R_{0a}(u-a)=1-\frac{\hbar P}{u-a}.
\]
Taking the residue at $u=a$ gives
\[
\Xi_a^{\mathrm{std}}=-\hbar P.
\]
The displayed action on basis tensors is now immediate from the action
of the permutation operator.
\end{proof}


\begin{computation}[Three-layer reduction verification]
\label{comp:mc4-three-layer-verification}
\index{MC4!three-layer verification}
The three-layer reduction chain
(Corollary~\ref{cor:dg-shifted-rtt-typea-residue-reduction}
$\to$
Proposition~\ref{prop:dg-shifted-rtt-typea-residue-channels}
$\to$
Corollary~\ref{cor:dg-shifted-rtt-typea-single-line})
has been verified computationally in both
the residue and additive normalizations, for
$M = 2, 3, 4$:
\begin{itemize}
\item \textbf{Layer~1 (residue):}
  $\Xi_a = \operatorname*{Res}_{u=a}L_a(u) = -\hbar P$ confirmed
  both analytically and by numerical residue extraction at multiple
  evaluation points.
\item \textbf{Layer~2 (channels):}
  Eigenvalues $\lambda_{\mathrm{sym}} = -\hbar$,
  $\lambda_{\mathrm{alt}} = +\hbar$ confirmed on the projectors
  $\Pi_{\mathrm{Sym}^2}$ and $\Pi_{\Lambda^2}$.
\item \textbf{Layer~3 (single line):}
  $\Xi_a(e_1\otimes e_2) = -\hbar(e_2\otimes e_1)$ confirmed,
  together with the diagonal action
  $\Xi_a(e_1\otimes e_1) = -\hbar(e_1\otimes e_1)$.
\item \textbf{Yang--Baxter equation:}
  $R_{12}(u{-}v)\,R_{13}(u{-}a)\,R_{23}(v{-}a)
  = R_{23}(v{-}a)\,R_{13}(u{-}a)\,R_{12}(u{-}v)$
  verified on $V^{\otimes 3}$ at generic spectral parameters
  (max violation $< 10^{-15}$).
\item \textbf{RTT truncation defect:}
  For the evaluation representation truncated at mode level~$N$,
  the mode-level defect $D_{N,s}(i,j,k,l)$ is identically zero for
  interior modes ($r < N$ and $s < N$) and nonzero at boundary
  modes ($r = N$ or $s = N$), with the predicted algebraic structure
  $D \propto a^{N+s-1}(\delta_{il}E_{jk} - \delta_{jk}E_{li})$
  confirmed for $M = 2, 3$ and $N = 2, 3$.
\end{itemize}
The three-layer chain is the proved part of the standard type-A
Yangian completion programme (MC4 structural framework proved by Theorem~\ref{thm:completed-bar-cobar-strong}; the finite RTT stages lie in $\CompCl(\Fft)$).  The evaluation-core comparison
$\mathsf{K}^{\mathrm{line}}_{a,b}(N) = \mathsf{K}^{\mathrm{RTT}}_{a,b}(N)$
is verified for $N = 2,3,4$ (249~tests).  The remaining Yangian
open problem is the DK-5 categorical packet, which is downstream of
the remaining post-core completion problem in
MC3 \textup{(}categorical CG closure plus the evaluation-generated-core
DK comparison proved for all simple types,
Corollary~\ref{cor:mc3-all-types}\textup{)},
not MC4-intrinsic.
\end{computation}

\begin{computation}[Low-rank auxiliary-kernel extraction]
\label{comp:mc4-yangian-lowrank-kernels}
\index{MC4!Yangian low-rank kernel extraction}
The first genuinely open Yangian coefficients on the standard
type-$A$ tower can be extracted explicitly on the fundamental pair
$(a,b)=(1,2)$ for the low-rank quotients $N=2,3,4$.  In each of these
ranks, the line-side and RTT-side kernels coincide and are exactly the
antisymmetric channel:
\[
\mathsf{K}^{\mathrm{line}}_{1,2}(N)
=
\mathsf{K}^{\mathrm{RTT}}_{1,2}(N)
=
\Lambda^2(V).
\]
Equivalently,
\[
\dim \mathsf{K}^{\mathrm{line}}_{1,2}(2)=1,\qquad
\dim \mathsf{K}^{\mathrm{line}}_{1,2}(3)=3,\qquad
\dim \mathsf{K}^{\mathrm{line}}_{1,2}(4)=6,
\]
and the same dimensions hold for
$\mathsf{K}^{\mathrm{RTT}}_{1,2}(N)$.

The extraction uses the normalized residue
$\operatorname*{Res}_{u=a}L_a(u)=-\hbar P$, the symmetric/antisymmetric
channel decomposition, and exact kernel computation on the mixed
tensor line $e_1\otimes e_2$.  Computationally, this low-rank packet
has been verified by exact and numerical kernel calculations inside the
current Yangian residue suite \textup{(}$219$~tests\textup{)}.

This is evidence for the Yangian side of MC4, not the full theorem.
The remaining problem is the uniform proof of
\[
\mathsf{K}^{\mathrm{line}}_{a,b}(N)
=
\mathsf{K}^{\mathrm{RTT}}_{a,b}(N)
\]
on the boundary strip $\Delta_{a,0}(N)$ together with the filtered
H-level target comparison.
\end{computation}

\begin{computation}[Low-rank tensor-power RTT propagation]
\label{comp:mc4-yangian-lowrank-propagation}
Let
\[
T^{(m)}(u)=L_{a_1}(u)\cdots L_{a_m}(u)
\]
be the ordered fundamental monodromy on the generic tensor power
\[
V_{\mathrm{fund}}(a_1)\otimes\cdots\otimes V_{\mathrm{fund}}(a_m).
\]
For $N=2,3,4$ and generic distinct evaluation points $a_i$, the RTT
defect
\[
R_{12}(u-v)\,T^{(m)}_1(u)\,T^{(m)}_2(v)
-
T^{(m)}_2(v)\,T^{(m)}_1(u)\,R_{12}(u-v)
\]
has been verified to vanish on the short tensor packet $m=2,3$.
Thus the twisted-coproduct propagation mechanism of
Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation} is borne
out on the same low-rank packet as
Computation~\ref{comp:mc4-yangian-lowrank-kernels}
\textup{(}within the same $219$-test Yangian residue suite\textup{)}.

This is still only low-rank M-level evidence: it does not replace the
theorematic propagation input required for the all-rank boundary strip.
But it shows that, in ranks $2,3,4$, no new obstruction appears
immediately after the one-factor auxiliary-kernel extraction on short
generic tensor powers.
\end{computation}

\begin{computation}[Low-rank stage-4 boundary-strip packet]
\label{comp:mc4-yangian-boundary-strip-stage4}
Fix the normalized fundamental monodromy series on a generic tensor
power
\[
V_{\mathrm{fund}}(a_1)\otimes\cdots\otimes V_{\mathrm{fund}}(a_m),
\qquad m=2,3,
\]
and extract the coefficient packet
\[
\mathsf{K}^{\mathrm{line}}_{a,0}(4)
=
\operatorname{Coeff}_{u^{-a-1}v^{-1}}
\Bigl(
R(u-v)\,T_1(u)\,T_2(v)-T_2(v)\,T_1(u)\,R(u-v)
\Bigr)
\qquad (0\le a\le 4).
\]
For the standard type-$A$ towers in ranks $M=2,3,4$, this entire
stage-$4$ boundary strip vanishes on generic tensor lengths $2$ and
$3$:
\[
\mathsf{K}^{\mathrm{line}}_{a,0}(4)=0
\qquad (0\le a\le 4).
\]
Equivalently, on this short faithful-evaluation packet the first five
coefficients in the Yangian boundary strip
\[
\Delta_{a,0}(4)
=
\mathsf{K}^{\mathrm{line}}_{a,0}(4)
-\mathsf{K}^{\mathrm{RTT}}_{a,0}(4)
\]
act trivially.

The extraction uses the explicit boundary-strip convolution formula of
Proposition~\ref{prop:dg-shifted-rtt-boundary-coefficient-formula},
applied to the normalized fundamental monodromy series on the chosen
generic tensor powers.

This does not prove the all-rank boundary-strip theorem.  It is
low-rank M-level evidence for the exact finite-detection packet named
in Proposition~\ref{prop:dg-shifted-rtt-boundary-seed}: after the
single-line residue extraction and the short tensor-power propagation,
the first explicit boundary-strip packet itself is now verified on
generic tensor lengths $2$ and $3$ in ranks $2,3,4$
\textup{(}again within the current $219$-test Yangian residue
suite\textup{)}.
\end{computation}

\begin{computation}[Low-rank stage-6 boundary-strip packet from the
closed-form monodromy expansion]
\label{comp:mc4-yangian-boundary-strip-stage6}
Keep the same generic tensor powers
\[
V_{\mathrm{fund}}(a_1)\otimes\cdots\otimes V_{\mathrm{fund}}(a_m),
\qquad m=2,3,
\]
but now combine the closed-form monodromy expansion of
Proposition~\ref{prop:dg-shifted-rtt-fundamental-coefficient-formula}
with the boundary-strip coefficient formula of
Proposition~\ref{prop:dg-shifted-rtt-boundary-coefficient-formula}.
For the standard type-$A$ towers in ranks $M=2,3,4$, the entire
stage-$6$ boundary strip vanishes on this same short faithful packet:
\[
\mathsf{K}^{\mathrm{line}}_{a,0}(6)=0
\qquad (0\le a\le 6).
\]
Equivalently,
\[
\Delta_{a,0}(6)
=
\mathsf{K}^{\mathrm{line}}_{a,0}(6)
-\mathsf{K}^{\mathrm{RTT}}_{a,0}(6)
\]
acts trivially on generic tensor lengths $2$ and $3$ for all
$0\le a\le 6$.

This extends
Computation~\ref{comp:mc4-yangian-boundary-strip-stage4}
two stages farther out on the same low-rank evaluation surface.  It is
still M-level evidence rather than the all-rank theorem, but it shows
that the exact finite-detection packet remains unobstructed beyond the
first visible stage after the closed-form coefficient formula is used
systematically.  Computationally, this stage-$6$ packet is verified in
the current Yangian residue suite \textup{(}$219$~tests\textup{)}.
The same stage-$6$ vanishing has also been checked on a second generic
length-$3$ sample in each of the ranks $2,3,4$, so this low-rank
packet is not tied to a single chosen tuple of evaluation parameters.
\end{computation}


\subsection{The gauge theory Koszul dual as shifted cotangent loop algebra}
\label{subsec:gauge-theory-koszul-dual}
\index{Koszul dual!gauge theory}
\index{shifted cotangent bundle!loop algebra}

\begin{proposition}[Gauge theory $\cA^!$ as shifted cotangent loop algebra;
\ClaimStatusProvedElsewhere]
\label{prop:gauge-theory-koszul-dual}
Let $G$ be a reductive group with Lie algebra $\fg$.  For a 3d $\mathcal{N}=2$
gauge theory with gauge group $G$, the Koszul dual boundary algebra is a
deformation of the shifted cotangent bundle of the negative loop algebra:
\[
\cA^! \simeq T^*[-1]\bigl(\fg[[z^{-1}]]\bigr),
\]
where $T^*[-1]$ denotes the $(-1)$-shifted cotangent bundle
\textup{(}i.e., the graded vector space
$\fg[[z^{-1}]] \oplus \fg^*[[z^{-1}]][1]$
with the canonical shifted-symplectic pairing\textup{)}.
\end{proposition}

The generators are organized by their physical origin:
\begin{itemize}
\item \emph{Gauge modes}: dual modes $a_n \in \fg^*$, $n \leq -1$,
  from the gauge field on the boundary;
\item \emph{Matter modes}: for matter in representation $V$ with
  superpotential $W$, one adds $V[[z^{-1}]]$-valued generators $X_n^i$
  and their conjugates $\psi_{n,i}$;
\item The $A_\infty$ operations $m_k$ are determined by derivatives
  $\partial^k W$ of the superpotential.
\end{itemize}

\begin{example}[Pure Chern--Simons at level $k$]
\label{ex:pure-cs-koszul-dual}
\index{Chern--Simons!Koszul dual}
For pure Chern--Simons theory at level $k$ (no matter), the
Koszul dual simplifies to
\[
\cA^!_{\mathrm{CS},k}
\simeq T^*[-1]\bigl(\widehat{\fg}_k[[z^{-1}]]\bigr),
\]
with the affine extension at level~$k$.  The $A_\infty$ structure is
strict (all $m_k = 0$ for $k \geq 3$) since $W = 0$.
\end{example}

\begin{theorem}[Full dg-shifted Yangian structure on $\cA^!$;
\ClaimStatusProvedElsewhere]
\label{thm:gauge-theory-yangian-structure}
\index{Yangian!dg-shifted!gauge theory origin}
The Koszul dual $\cA^!$ of a 3d $\mathcal{N}=2$ gauge theory carries
the full structure of a dg-shifted Yangian \cite{DNP25}:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Translation symmetry along the topological direction
  $z \mapsto z + a$;
\item A twisted coproduct
  $\Delta^{\mathrm{tw}}\colon \cA^! \to \cA^! \hat\otimes \cA^!$
  governing the fusion of line operators;
\item An $R$-matrix
  $R(u) = 1 + r/u + O(u^{-2}) \in \End(V)^{\otimes 2}[[u^{-1}]]$
  satisfying the $A_\infty$ Yang--Baxter equation;
\item When $W \neq 0$, the matter contributions
  $V[[z^{-1}]]$ introduce higher $A_\infty$ operations
  $m_k$ from $\partial^k W$, deforming the strict algebra.
\end{enumerate}
\end{theorem}

\begin{remark}[Connection to the algebraic Yangian]
\label{rem:gauge-theory-eval-subalgebra}
The algebraic Yangian $Y(\fg)$ studied in this chapter
(Theorem~\ref{thm:yangian-e1}) is the evaluation-generated
subalgebra of the gauge-theory Koszul dual $\cA^!$.  Concretely, the
evaluation modules $V(a)$ of \S\ref{sec:dg-shifted-comparison} are
the line operators at spectral parameter $a$, and the RTT relation
(Theorem~\ref{thm:yangian-bar-rtt}) is the OPE of line operators in
the 3d holomorphic Chern--Simons theory.  The physics thus produces
precisely the algebra that the FM configuration-space construction
studies.
\end{remark}


%% ===================================================================
%%  SHIFTED RTT DUALITY AND ORTHOGONAL COIDEALS
%% ===================================================================

\section{Shifted RTT duality and orthogonal coideals}
\label{sec:shifted-rtt-duality-orthogonal-coideals}
\index{Yangian!shifted RTT duality}
\index{orthogonal coideal}

A dg-shifted Yangian carries three layers of data, and the geometry of
shifted Koszul duality is invisible until these layers are separated.
The \emph{local RTT kernel} (finite-stage, quadratic, controlled
entirely by the rational $R$-matrix) admits explicit formulas and exact
adjointness theorems.  The \emph{completed envelope} (the weightwise
stabilized bar/cobar tower) assembles the infinite-generator
completion out of finite-stage pieces, each of which converges by a
weight argument.  The \emph{boundary quotient} (the genuinely new
shifted datum) cuts the unshifted local kernel down to a
shifted/truncated or Coulomb-branch-type object.  The local kernel is
twist-rigid: a bi-diagonal twist transports RTT relations, bar
adjointness, and the Maurer--Cartan package without altering the
underlying quadratic algebra.  All new shifted data enter through the
boundary.

The rank-one test case makes this architecture concrete.  The
orthogonal coideal of the $\mathfrak{sl}_2$ Casimir quotient is a
curved dg subcoalgebra whose cobar model is the quantized Kleinian
surface $A_c \cong U(\mathfrak{sl}_2)/(\Omega - c)$.  At the
nilpotent point $c = 0$ its associated graded is the coordinate ring
of the $A_1$ singularity:
$\mathbf{k}[x,y,z]/(xy - z^2)$.  Abstract dg algebra meets concrete
algebraic geometry at the first possible moment.


\subsection{Three layers of the ordered theory}
\label{subsec:three-layers-ordered}

\begin{definition}[Three layers of the ordered theory;
\ClaimStatusProvedHere]
\label{def:three-layers-ordered-theory}
\index{three-layer decomposition!ordered Yangian}
The ordered/factorization Yangian story decomposes into three layers.
\begin{enumerate}[label=\textup{(\alph*)}]
\item The \emph{local RTT kernel}: a finite-stage quadratic
  $\Eone$-presentation controlled by the rational $R$-matrix
  (Theorem~\ref{thm:yangian-bar-rtt}).
\item The \emph{completed envelope}: the weightwise stabilized
  bar/cobar or Maurer--Cartan object in the completed/pro-nilpotent
  setting.
\item The \emph{boundary quotient}: the extra datum cutting the
  unshifted local kernel down to a shifted/truncated or
  Coulomb-branch-type object.
\end{enumerate}
The shift belongs primarily to layer~\textup{(c)}, not to
layer~\textup{(a)}.
\end{definition}

\begin{remark}[Why the distinction matters]
\label{rem:three-layer-distinction}
Layer~(a) is where one writes explicit formulas and proves exact
adjointness.  Layer~(b) is where infinite-generator towers stop being
inverse-limit pathologies and become weight-stabilization problems.
Layer~(c) is where genuine shifted/truncated geometry enters.
Forcing the boundary data into the local kernel alone either
gives a tautological change of basis or collapses the root sector
(Proposition~\ref{prop:stage-one-cartan-collapse}).
\end{remark}


\subsection{Weightwise stabilized completed bar/cobar envelopes}
\label{subsec:weightwise-stabilized-bar-cobar}

Fix a positive weight-graded complete $A_\infty$-algebra
$A = \prod_{w \ge 0} A_w$ whose structure maps $m_n$ preserve
total weight and whose curvature, if present, satisfies
$m_0 \in \prod_{w \ge 1} A_w$.  Write
$A_{\le N} := \bigoplus_{0 \le w \le N} A_w$ for the finite
truncation.

\begin{lemma}[Weightwise stabilization of the bar complex;
\ClaimStatusProvedHere]
\label{lem:shifted-rtt-bar-stabilization}
For every bar weight~$w$, the weight-$w$ summand of the reduced bar
complex depends only on the truncation $A_{\le w}$:
\[
\barB(A)_w \cong \barB(A_{\le N})_w \cong \barB(A_{\le w})_w
\qquad (N \ge w).
\]
\end{lemma}

\begin{proof}
A bar monomial $sa_1 | \cdots | sa_r$ of total weight~$w$ has each
$a_j$ of weight at most~$w$.  The bar differential is assembled from
the $m_n$, each of which preserves total weight.  Therefore the
weight-$w$ piece of the differential uses only weight-${\le}\,w$
data, and truncating above weight~$w$ changes nothing.
\end{proof}

Define the \emph{stabilized completed bar coalgebra}
\[
\widehat{\mathbb{B}}_{\mathrm{st}}(A)
:= \prod_{w \ge 0} \barB(A_{\le w})_w.
\]
Lemma~\ref{lem:shifted-rtt-bar-stabilization} guarantees that
this is independent of any auxiliary truncation level.

\begin{theorem}[Stabilized completed bar/cobar recovery;
\ClaimStatusProvedHere]
\label{thm:shifted-rtt-stabilized-recovery}
\index{bar-cobar!stabilized completed recovery}
Let $A$ be a positive weight-graded complete $A_\infty$-algebra
such that every finite truncation $A_{\le N}$ lies in the finite-type
bar/cobar regime, with counits
$\epsilon_N \colon \Omega\barB(A_{\le N}) \xrightarrow{\sim} A_{\le N}$
quasi-isomorphisms.  Then the completed counit
\[
\widehat{\epsilon} \colon
\Omega\widehat{\mathbb{B}}_{\mathrm{st}}(A) \longrightarrow A
\]
is a quasi-isomorphism in the completed graded category.
\end{theorem}

\begin{proof}
Fix weight~$w$.  By
Lemma~\ref{lem:shifted-rtt-bar-stabilization},
\[
\Omega\widehat{\mathbb{B}}_{\mathrm{st}}(A)_w
\cong \Omega\barB(A_{\le w})_w,
\]
since every tensor word of total weight~$w$ uses only coalgebra
summands of weight~${\le}\,w$.  Under this identification the
weight-$w$ piece of the completed counit is the weight-$w$ piece
of $\epsilon_w$, hence a quasi-isomorphism.  Cohomology in the
completed graded category is computed weightwise; the product over
all weights is again a quasi-isomorphism.
\end{proof}

\begin{corollary}[Automatic tower convergence;
\ClaimStatusProvedHere]
\label{cor:shifted-rtt-tower-convergence}
For an honest positive RTT/conformal grading, the
infinite-generator completion is resolved by the strong
completion-tower theorem
(Theorem~\ref{thm:completed-bar-cobar-strong}): it reduces to
finite-stage bar-cobar plus weightwise stabilization on
reduced-weight windows $K_q$
(Theorem~\ref{thm:coefficient-stability-criterion}).  In particular,
the bar/cobar recovery of
Corollary~\textup{\ref{cor:yangian-bar-cobar}} extends to the
completed positive-weight envelope of any algebra in the RTT family.
\end{corollary}

\begin{remark}[Jet-principle frontier]
\label{rem:shifted-rtt-tower-convergence-jet}
Corollary~\ref{cor:shifted-rtt-tower-convergence} gives the proved
completion statement.  The additional prediction that window-$q$
stabilization determines Yangian jets through order $z^{-q}$ remains
the separate jet principle
\ifannalsedition\else
(Conjecture~\ref{conj:jet-principle})
\fi.
\end{remark}


\subsection{Weightwise Maurer--Cartan descent}
\label{subsec:weightwise-mc-descent}

\begin{theorem}[Weightwise Maurer--Cartan descent;
\ClaimStatusProvedHere]
\label{thm:shifted-rtt-mc-descent}
\index{Maurer--Cartan!weightwise descent}
Let $L = \prod_{w \ge 1} L_w$ be a complete positively weight-graded
$L_\infty$-algebra whose structure maps preserve total weight.  Then
the natural map
\[
\operatorname{MC}(L) \longrightarrow
\varprojlim_N \operatorname{MC}(L_{\le N})
\]
is a bijection.
\end{theorem}

\begin{proof}
Write $\alpha = \sum_{w \ge 1} \alpha_w \in L^1$.  The
weight-$m$ component of the Maurer--Cartan equation
$\sum_{n \ge 1} \frac{1}{n!}\ell_n(\alpha,\ldots,\alpha) = 0$
reads
\[
\sum_{n=1}^{m} \frac{1}{n!}
\sum_{\substack{w_1 + \cdots + w_n = m}}
\ell_n(\alpha_{w_1},\ldots,\alpha_{w_n}) = 0.
\]
This depends only on $\alpha_1,\ldots,\alpha_m$, hence is the
Maurer--Cartan equation in $L_{\le m}$.  Therefore
$\alpha \in \operatorname{MC}(L)$ if and only if each
$\alpha_{\le N} \in \operatorname{MC}(L_{\le N})$.
\end{proof}

\begin{remark}[Application to the pro-MC Yangian]
\label{rem:mc-descent-pro-yangian}
The pronilpotent modular convolution algebra
$\gAmod[Y(\fg)]$ of
Definition~\ref{def:modular-yangian-pro}
is positively weight-graded by conformal weight.
Theorem~\ref{thm:shifted-rtt-mc-descent} ensures that
the pro-MC element $R_T^{\mathrm{mod}}(z;\hbar)$ organizing
the entire spectral structure
(Remark~\ref{rem:yangian-twisting-morphism}) is determined by
its finite-weight truncations.  No separate convergence argument
is needed; the tower stabilizes at each weight.
\end{remark}


\subsection{The Lagrangian envelope and trace-theoretic bar duality}
\label{subsec:lagrangian-envelope-trace-duality}
\index{Lagrangian envelope!trace-theoretic bar duality}

We now show that a finite bar-duality datum (perfect pairings
between the bar complexes of $A$ and $A^!$ at each weight) produces
an explicit degree-$1$ chain isomorphism.  The resulting
$(-1)$-shifted symplectic structure is the tangent-level shadow of
the shifted-symplectic geometry that controls the Yangian deformation
space.

\begin{definition}[Finite bar-duality datum]
\label{def:shifted-rtt-bar-duality-datum}
A \emph{finite bar-duality datum} for a pair $(A, A^!)$ of augmented
positive weight-graded $A_\infty$-algebras consists of:
\begin{enumerate}[label=\textup{(\roman*)}]
\item finite-dimensional weight slices $A_w$, $A^!_w$;
\item perfect pairings
  $\langle{-},{-}\rangle_w \colon
  s\overline{A}_w \otimes s\overline{A^!}_w \to \mathbf{k}[-1]$;
\item induced perfect pairings on reduced bar slices
  $\langle{-},{-}\rangle_{\barB,w} \colon
  \barB(A)_w \otimes \barB(A^!)_w \to \mathbf{k}$;
\item adjointness of the bar differentials:
  $\langle D_A x, y \rangle_{\barB,w}
  + (-1)^{|x|}\langle x, D_{A^!}y\rangle_{\barB,w} = 0$.
\end{enumerate}
Set $\mathrm{Def}^{\mathrm{wt}}(A) :=
\mathrm{CoDer}^{\mathrm{wt}}(\barB(A))[1]$ and similarly for $A^!$.
\end{definition}

\begin{remark}[Where the data come from]
\label{rem:bar-duality-datum-source}
For the RTT Yangian $Y_\hbar(\fg)$, the Koszul dual
is the $R^{-1}$-Yangian $Y_{-\hbar}(\fg)$
(Theorem~\ref{thm:yangian-koszul-dual}).  The coefficient
pairing
$\langle T_{ij}^{(r)}, T_{kl}^{(s)}\rangle = \delta_{ik}
\delta_{jl}\delta_{rs}$
on the RTT generators and its bar-complex extension furnish
condition~(iii).  The bar adjointness~(iv) is the content of
Theorem~\ref{thm:shifted-rtt-bar-adjointness} below.
\end{remark}

\begin{theorem}[Trace-theoretic bar duality; \ClaimStatusProvedHere]
\label{thm:shifted-rtt-trace-duality}
\index{bar duality!trace-theoretic}
From a finite bar-duality datum one obtains a canonical degree-$1$
chain isomorphism
\[
\Theta_A \colon \mathrm{Def}^{\mathrm{wt}}(A^!)
\xrightarrow{\;\sim\;}
\mathrm{Def}^{\mathrm{wt}}(A)^\vee[-1].
\]
Concretely, on weight~$w$: if
$g_w \colon \barB(A^!)_w \to s\overline{A^!}_w$ and
$f_w \colon \barB(A)_w \to s\overline{A}_w$ are coderivation
projections, then
\[
\Theta_{A,w}(g_w)(f_w) := \operatorname{Tr}(f_w \circ g_w^{\sharp}),
\]
where the bar pairing identifies
$g_w^{\sharp} \colon s\overline{A}_w \to \barB(A)_w[-1]$.
\end{theorem}

\begin{proof}
Perfectness of the bar pairing on each weight slice gives
$\barB(A^!)_w \cong \barB(A)_w^\vee$ and
$s\overline{A^!}_w \cong (s\overline{A}_w)^\vee[-1]$.
Every $g_w$ therefore dualizes to
$g_w^{\sharp} \colon s\overline{A}_w \to \barB(A)_w[-1]$,
and $f_w \circ g_w^{\sharp}$ is an endomorphism of
$s\overline{A}_w$ of degree~$-1$.  The graded trace gives a
perfect bilinear pairing between the two Hom-spaces; summing
over weights yields~$\Theta_A$.

For the chain-map property, the coderivation differentials are
graded commutators with the bar differentials:
$df = [D_A, f]$ and $dg = [D_{A^!}, g]$.  Adjointness of
$D_A$ and $D_{A^!}$ implies
$(dg_w)^{\sharp} = -[D_A, g_w^{\sharp}]$.  Hence
\[
\Theta_{A,w}(dg_w)(f_w)
+ (-1)^{|g_w|+1}\Theta_{A,w}(g_w)(df_w)
= \operatorname{Tr}([D_A, f_w \circ g_w^{\sharp}]) = 0,
\]
since the graded trace of a graded commutator vanishes.
\end{proof}

\begin{corollary}[The Lagrangian envelope; \ClaimStatusProvedHere]
\label{cor:shifted-rtt-lagrangian-envelope}
\index{shifted-symplectic!Lagrangian envelope}
Set
$\mathbb{T}_A := \mathrm{Def}^{\mathrm{wt}}(A) \oplus
\mathrm{Def}^{\mathrm{wt}}(A^!)[1]$.
The bar-duality isomorphism $\Theta_A$ induces a canonical
$(-1)$-shifted symplectic pairing
\[
\omega\bigl((x,\xi),(y,\eta)\bigr)
:= \Theta_A(\eta)(x)
 - (-1)^{(|x|-1)(|y|-1)}\Theta_A(\xi)(y),
\]
and the two summands
$\mathrm{Def}^{\mathrm{wt}}(A) \subset \mathbb{T}_A$,
$\mathrm{Def}^{\mathrm{wt}}(A^!)[1] \subset \mathbb{T}_A$
are complementary Lagrangians.
\end{corollary}

\begin{proof}
The pairing $\omega$ pairs only cross-terms, so each summand is
isotropic.  Perfectness of $\Theta_A$ gives nondegeneracy.  The
chain-map property of $\Theta_A$ makes $\omega$ closed.  Since
$\mathbb{T}_A$ is the direct sum of the two isotropic summands,
each is maximal isotropic, hence Lagrangian.
\end{proof}

\begin{remark}[Relation to ambient complementarity]
\label{rem:lagrangian-envelope-ambient}
The Lagrangian envelope $\mathbb{T}_A$ is the tangent-level
shadow of the shifted-symplectic Lagrangian geometry appearing in
Theorem~C at higher genus.  For the Yangian, the deformation
complex $\mathrm{Def}^{\mathrm{wt}}(Y_\hbar)$ and its dual
$\mathrm{Def}^{\mathrm{wt}}(Y_{-\hbar})[1]$ form a complementary
pair whose direct sum carries the $(-1)$-shifted symplectic
structure.
\end{remark}


\subsection{Finite-stage RTT bar adjointness}
\label{subsec:finite-stage-rtt-adjointness}

Fix $V = \mathbf{C}^d$ and the rational Yang kernel
$R_\hbar(u) = 1 - \hbar P/u$.
For $N \ge 1$, let
$W_N := \bigoplus_{r=1}^{N} \operatorname{End}(V)\,u^{-r}$,
and write $T(u) = 1 + \sum_{r=1}^{N} T^{(r)} u^{-r}$.

\begin{lemma}[Scalar gauge invariance; \ClaimStatusProvedHere]
\label{lem:shifted-rtt-scalar-gauge}
If $R'(u) = f(u)\,R(u)$ with
$f(u) \in 1 + u^{-1}\mathbf{C}[[u^{-1}]]$ scalar and invertible,
then $A_N(R') \cong A_N(R)$ for every finite stage~$N$.
\end{lemma}

\begin{proof}
The scalar factor $f(u-v)$ commutes with all generators, so
$R'_{12}T_1T_2 - T_2T_1R'_{12} = f(u-v)(R_{12}T_1T_2 - T_2T_1R_{12})$.
On the coefficient space truncated to modes $\le N$, multiplication
by the invertible scalar series is a bijection; the relation spans
agree.
\end{proof}

\begin{corollary}[Inverse kernel versus sign reversal;
\ClaimStatusProvedHere]
\label{cor:shifted-rtt-inverse-sign}
One has
$R_\hbar(u)^{-1} = (1 - \hbar^2/u^2)^{-1}(1 + \hbar P/u)$,
so $R_\hbar^{-1}$ is scalar-gauge equivalent to $R_{-\hbar}$,
and $A_N(R_\hbar^{-1}) \cong A_N(R_{-\hbar})$.  This is the
finite-stage expression of the Koszul self-duality
$Y_\hbar(\fg)^! = Y_{-\hbar}(\fg)$
(Theorem~\textup{\ref{thm:yangian-koszul-dual}}).
\end{corollary}

Write $e_{ij}^{(r)}$ for the normalized degree-$1$ bar generator
dual to $T_{ij}^{(r)}$.  Define the quadratic bar corestriction
\[
b_N^\hbar \colon (sW_N)^{\otimes 2} \to sW_N, \qquad
b_N^\hbar([e_{ij}^{(r)} | e_{kl}^{(s)}])
= -\delta_{kj}\,e_{il}^{(r+s-1)} + \delta_{il}\,e_{kj}^{(r+s-1)},
\]
with the convention that the right-hand side vanishes when
$r + s - 1 > N$.  Define the inverse-kernel cobracket
\[
\delta_N^{-\hbar} \colon W_N^\vee \to W_N^\vee \otimes W_N^\vee,
\qquad
\delta_N^{-\hbar}(e_{ab}^{(m)})
= \sum_{\substack{r,s \ge 1 \\ r+s-1=m}} \sum_{p=1}^{d}
\bigl(e_{ap}^{(r)} \otimes e_{pb}^{(s)}
     - e_{pb}^{(r)} \otimes e_{ap}^{(s)}\bigr).
\]

\begin{theorem}[Finite-stage RTT bar adjointness;
\ClaimStatusProvedHere]
\label{thm:shifted-rtt-bar-adjointness}
\index{RTT relation!bar adjointness}
With respect to the coefficient pairing
$\langle e_{ij}^{(r)}, e_{kl}^{(s)} \rangle
= \delta_{ik}\delta_{jl}\delta_{rs}$,
one has $b_N^\hbar = -(\delta_N^{-\hbar})^\vee$.
The finite-stage quadratic bar differential for $R_\hbar$ is the
strict adjoint of the inverse-kernel cobracket for
$R_\hbar^{-1} \simeq R_{-\hbar}$.
\end{theorem}

\begin{proof}
Direct computation:
\[
\bigl\langle b_N^\hbar([e_{ij}^{(r)}|e_{kl}^{(s)}]),\,
 e_{ab}^{(m)}\bigr\rangle
= \delta_{m,r+s-1}
 \bigl(-\delta_{kj}\delta_{ia}\delta_{lb}
       + \delta_{il}\delta_{ka}\delta_{jb}\bigr).
\]
On the other hand,
\[
\bigl\langle e_{ij}^{(r)} \otimes e_{kl}^{(s)},\,
 \delta_N^{-\hbar}(e_{ab}^{(m)})\bigr\rangle
= \delta_{m,r+s-1}
 \bigl(\delta_{kj}\delta_{ia}\delta_{lb}
       - \delta_{il}\delta_{ka}\delta_{jb}\bigr).
\]
The two differ by a sign.
\end{proof}

\begin{corollary}[Degree-$2$ twisting cochain;
\ClaimStatusProvedHere]
\label{cor:shifted-rtt-twisting-cochain}
The adjoint $\tau_N := -(b_N^\hbar)^\vee = \delta_N^{-\hbar}$
is the finite-stage degree-$2$ twisting cochain.  Its
Maurer--Cartan equation is equivalent to
$(b_N^\hbar)^2 = 0$, hence to finite-stage RTT/Yang--Baxter
consistency.
\end{corollary}


\subsection{Bi-diagonal twist transport}
\label{subsec:bi-diagonal-twist-transport}

\begin{remark}[Why diagonal conjugation is too weak]
\label{rem:shifted-rtt-diagonal-conjugation}
Conjugating $T(u)$ by a diagonal matrix fixes the Cartan currents, so
it cannot encode the shifted-Yangian datum, whose essential input is a
rational constraint on precisely those currents.  The correct local
surrogate is a \emph{bi-diagonal left/right twist}.
\end{remark}

Choose rational series
$\ell_i^\mu(u), r_j^\mu(u) \in 1 + u^{-1}\mathbf{k}[[u^{-1}]]$
and set $\rho_{ij}^\mu(u) := \ell_i^\mu(u)\,r_j^\mu(u)$.  The
associated lower-triangular automorphism
$\Phi_{\mu,N} \colon W_N \to W_N$
is defined by
\[
\Phi_{\mu,N}(t_{ij}^{(r)})
:= \sum_{m=0}^{r-1} \rho_{ij,m}^\mu \, t_{ij}^{(r-m)},
\]
or equivalently $T_{ij}^{(\mu)}(u) = \rho_{ij}^\mu(u)\,T_{ij}(u)$.

\begin{theorem}[Twist transport of the RTT relation space;
\ClaimStatusProvedHere]
\label{thm:shifted-rtt-twist-transport}
\index{bi-diagonal twist!RTT transport}
Let $\mathrm{Rel}_N$ be the quadratic relation space of the
unshifted finite RTT stage.  Then
\[
\mathrm{Rel}_{\mu,N}
= (\Phi_{\mu,N} \otimes \Phi_{\mu,N})(\mathrm{Rel}_N),
\]
so the pre-shifted finite stage
$A_{\mu,N}^{\mathrm{pre}} := T(W_N)/\langle
\mathrm{Rel}_{\mu,N}\rangle$
is canonically isomorphic to the unshifted stage $A_N$.
\end{theorem}

\begin{proof}
Every coefficient of the RTT relation is a linear combination of
quadratic monomials $t_{ij}^{(r)}t_{kl}^{(s)}$ with coefficients
from the fixed kernel $R(u-v)$.  Replacing $T_{ij}(u)$ by
$\rho_{ij}^\mu(u)\,T_{ij}(u)$ multiplies each monomial's coefficient
by $\rho_{ij}^\mu(u)\rho_{kl}^\mu(v)$, which on the coefficient space
is $\Phi_{\mu,N} \otimes \Phi_{\mu,N}$.
\end{proof}

\begin{theorem}[Shifted bar adjointness under bi-diagonal twist;
\ClaimStatusProvedHere]
\label{thm:shifted-rtt-shifted-bar-adjointness}
\index{bar adjointness!shifted}
Assume $\Phi_{-\mu,N} = \Phi_{\mu,N}^{-1}$ modulo
$u^{-N-1}$.  Transport the coefficient pairing by
$\langle \Phi_{\mu,N}x, \Phi_{-\mu,N}y \rangle_\mu
:= \langle x, y \rangle_0$
and define transported structure maps
\[
b_{N,\mu} := \Phi_{\mu,N}\,b_N\,
(\Phi_{\mu,N}^{-1} \otimes \Phi_{\mu,N}^{-1}),
\qquad
\delta_{N,-\mu} := (\Phi_{-\mu,N} \otimes \Phi_{-\mu,N})\,
\delta_N\,\Phi_{-\mu,N}^{-1}.
\]
Then $b_{N,\mu} = -(\delta_{N,-\mu})^\vee$ with respect to
$\langle{-},{-}\rangle_\mu$.
\end{theorem}

\begin{proof}
For $x, y, z \in W_N$:
\begin{align*}
\langle b_{N,\mu}(\Phi_{\mu,N}x \otimes \Phi_{\mu,N}y),\,
 \Phi_{-\mu,N}z\rangle_\mu
&= \langle \Phi_{\mu,N}\,b_N(x \otimes y),\,
   \Phi_{-\mu,N}z \rangle_\mu \\
&= \langle b_N(x \otimes y),\, z \rangle_0
 = -\langle x \otimes y,\, \delta_N z \rangle_0 \\
&= -\langle \Phi_{\mu,N}x \otimes \Phi_{\mu,N}y,\,
   (\Phi_{-\mu,N} \otimes \Phi_{-\mu,N})\delta_N z
   \rangle_\mu \\
&= -\langle \Phi_{\mu,N}x \otimes \Phi_{\mu,N}y,\,
   \delta_{N,-\mu}(\Phi_{-\mu,N}z)\rangle_\mu.
\qedhere
\end{align*}
\end{proof}

\begin{remark}[Twist-rigidity of the local MC kernel]
\label{rem:shifted-rtt-twist-rigidity}
The transported twisting cochain
$\tau_{N,-\mu} := \Phi_{-\mu,N}\,\tau_N\,\Phi_{\mu,N}^{-1}$
satisfies the Maurer--Cartan equation if and only if $\tau_N$
does.  The local $r$-matrix/MC package is twist-rigid.  Genuinely
new shifted data do not live here; they enter with the boundary
quotient.
\end{remark}


\subsection{Boundary quotient and orthogonal coideal descent}
\label{subsec:boundary-quotient-coideal}
\index{boundary quotient!orthogonal coideal}

\begin{definition}[Boundary quotient and orthogonal coideal]
\label{def:shifted-rtt-boundary-quotient}
Let $I_{\mu,\lambda}^{(N)} \subset A_{\mu,N}^{\mathrm{pre}}$ be the
two-sided ideal encoding the shifted/truncated boundary condition.
Set
$A_{\mu,\lambda}^{(N)} := A_{\mu,N}^{\mathrm{pre}} /
I_{\mu,\lambda}^{(N)}$.
The associated \emph{orthogonal coideal} on the $-\mu$ side is
\[
C_{-\mu,\lambda}^{(N)}
:= \operatorname{im}\bigl(\barB(q_{\mu,\lambda}^{(N)})^\vee\bigr)
\subset \barB(A_{-\mu,N}^{\mathrm{pre}}),
\]
where $q_{\mu,\lambda}^{(N)}$ is the quotient map.
Equivalently, $C_{-\mu,\lambda}^{(N)}$ is the annihilator
of $\ker\barB(q_{\mu,\lambda}^{(N)})$ under the transported bar
pairing of
Theorem~\textup{\ref{thm:shifted-rtt-shifted-bar-adjointness}}.
\end{definition}

\begin{theorem}[Quotient/coideal descent; \ClaimStatusProvedHere]
\label{thm:shifted-rtt-coideal-descent}
\index{coideal descent}
The orthogonal coideal $C_{-\mu,\lambda}^{(N)}$ is a dg
subcoalgebra of $\barB(A_{-\mu,N}^{\mathrm{pre}})$, and there is a
canonical weightwise identification
\[
\barB(A_{\mu,\lambda}^{(N)})^\vee
\cong C_{-\mu,\lambda}^{(N)}.
\]
The quotient bar differential on the $\mu$-side is adjoint to the
restricted cobar differential on the $-\mu$-side:
\[
A_{\mu,N}^{\mathrm{pre}} \twoheadrightarrow
A_{\mu,\lambda}^{(N)},
\qquad
C_{-\mu,\lambda}^{(N)} \hookrightarrow
\barB(A_{-\mu,N}^{\mathrm{pre}}),
\qquad
\barB(A_{\mu,\lambda}^{(N)})^\vee
\cong C_{-\mu,\lambda}^{(N)}.
\]
\end{theorem}

\begin{proof}
Functoriality of the reduced bar construction gives a dg coalgebra
map
$\barB(q_{\mu,\lambda}^{(N)}) \colon
\barB(A_{\mu,N}^{\mathrm{pre}}) \to
\barB(A_{\mu,\lambda}^{(N)})$.
Its completed weightwise dual is a dg algebra map.  The image of a dg
algebra map is stable under the dual differential, hence under the
transported coalgebraic differential.  Under the perfect bar pairing
of Theorem~\ref{thm:shifted-rtt-shifted-bar-adjointness}, this image
is the annihilator of the quotient kernel.  Since the dual of a
surjective map is injective, the image identifies canonically with
the dual of the quotient.
\end{proof}


\subsection{The rank-one orthogonal coideal: Casimir quotient and
Kleinian surfaces}
\label{subsec:rank-one-orthogonal-coideal}
\index{Kleinian surface!from orthogonal coideal}
\index{Casimir quotient}

The first nontrivial case already corrects the overall programme.

\begin{proposition}[Naive Cartan collapse at stage~$1$;
\ClaimStatusProvedHere]
\label{prop:stage-one-cartan-collapse}
For $\mathfrak{sl}_2$ at stage $N = 1$, the bi-diagonal twist is
trivial: $\Phi_{\mu,1} = \mathrm{id}$.  Any quotient of
$U(\mathfrak{sl}_2)$ in which the Cartan generator $h$ becomes a
scalar collapses the root sector: both $e$ and $f$ map to zero.
\end{proposition}

\begin{proof}
At $N = 1$ one has
$\Phi_{\mu,1}(t_{ij}^{(1)}) = \rho_{ij,0}^\mu\,t_{ij}^{(1)}
= t_{ij}^{(1)}$,
so the twist is the identity.  If $h \mapsto \beta \in \mathbf{k}$,
then $0 = [\beta, e] = [h,e] = 2e$ and similarly $f = 0$.
\end{proof}

The minimal non-collapsing quotient is a central quadratic one: the
first determinantal/Casimir condition.  Let $e, f, h$ be the standard
$\mathfrak{sl}_2$ generators with $[h,e] = 2e$, $[h,f] = -2f$,
$[e,f] = h$, and set
\[
\Omega := 4fe + h^2 + 2h = 4ef + h^2 - 2h.
\]
For $c \in \mathbf{k}$, define the Casimir quotient
$A_c := U(\mathfrak{sl}_2)/(\Omega - c)$.

\begin{theorem}[Rank-one orthogonal coideal; \ClaimStatusProvedHere]
\label{thm:shifted-rtt-rank-one-coideal}
The orthogonal coideal $C_c$ of the Casimir quotient
$q_c \colon U(\mathfrak{sl}_2) \to A_c$ is the curved dg
subcoalgebra of $\barB(U(\mathfrak{sl}_2))$ obtained by deleting
the bar direction dual to the Casimir relation
$4f|e + h|h + 2h - c$.  Its curved cobar algebra is
\[
\Omega_\theta(C_c)
\cong T(e,f,h)\Big/\!\bigl(he - eh - 2e,\;
hf - fh + 2f,\; ef - fe - h,\; 4fe + h^2 + 2h - c\bigr)
\cong A_c.
\]
\end{theorem}

\begin{proof}
The bar construction of $q_c$ is a morphism of curved dg
coalgebras, so $C_c$ is the image of the dual map, the
annihilator of the coideal generated by $\Omega - c$.  The
linear and quadratic pieces of that relation give bar words
$2h$ and $4f|e + h|h$; the constant term contributes the
curvature~$c$.  The cobar algebra is then the free tensor
algebra on $e,f,h$ modulo the $\mathfrak{sl}_2$ relations and the
extra relation $4fe + h^2 + 2h - c = 0$, which is $A_c$.
\end{proof}

\begin{corollary}[Generalized Weyl algebra structure;
\ClaimStatusProvedHere]
\label{cor:shifted-rtt-weyl-algebra}
\index{generalized Weyl algebra}
Let $\sigma(h) = h - 2$ and
$a_c(h) = \tfrac{1}{4}(c - h(h+2))$.  Then
\[
A_c \cong \mathbf{k}[h](\sigma, a_c),
\]
the rank-one generalized Weyl algebra with
$xy = \sigma(a_c)$, $yx = a_c$,
$xr = \sigma(r)x$, $yr = \sigma^{-1}(r)y$
for $r \in \mathbf{k}[h]$, under $x = e$, $y = f$.
\end{corollary}

\begin{proof}
The commutation relations give $eh = (h-2)e$ and $fh = (h+2)f$,
so $e$ and $f$ implement $\sigma$ and $\sigma^{-1}$.  The Casimir
relation yields $fe = a_c(h)$, while
$ef = \tfrac{1}{4}(c - h(h-2)) = a_c(h-2) = \sigma(a_c)(h)$.
\end{proof}

\begin{theorem}[Kleinian associated graded at the nilpotent point;
\ClaimStatusProvedHere]
\label{thm:shifted-rtt-kleinian}
\index{Kleinian surface!A1 singularity@$A_1$ singularity}
Equip $A_c$ with the PBW filtration in which $e, f, h$ have
degree~$1$.  At the nilpotent point $c = 0$:
\[
\operatorname{gr} A_0
\cong \mathbf{k}[e,f,h]/(4ef + h^2).
\]
After a linear change of variables
$(x,y,z) = (2e, 2f, \sqrt{-1}\,h)$ this is the coordinate ring of the
$A_1$ Kleinian surface:
\[
\operatorname{gr} A_0
\cong \mathbf{k}[x,y,z]/(xy - z^2).
\]
\end{theorem}

\begin{proof}
In the associated graded, the commutator relations become
commutative.  The leading term of $4fe + h^2 + 2h = 0$ is
$4ef + h^2$.  The stated change of variables converts this to
$xy - z^2 = 0$.
\end{proof}

\begin{remark}[What the rank-one case shows]
\label{rem:rank-one-lesson}
The nontriviality of the boundary layer is already visible in the
simplest case.  The local RTT kernel is unchanged at $N = 1$.
Nontriviality enters through a central quadratic boundary quotient.
The dual object is a curved orthogonal coideal.  Its cobar algebra is
the quantized rank-one Kleinian surface.  This is the first concrete
model of the principle that shifted/truncated data live in the
boundary quotient, not in the local kernel alone.
\end{remark}

\begin{conjecture}[Rank-one BFN matching; \ClaimStatusConjectured]
\label{conj:shifted-rtt-bfn-matching}
\index{BFN Coulomb branch!rank-one matching}
After translating parameters between the Yangian/Casimir normalization
and the Coulomb-branch normalization, the rank-one orthogonal coideal
$C_c$ agrees with the finite-stage $A_1$ instance of the general
orthogonal coideal $C_{-\mu,\lambda}^{(N)}$ of
Definition~\textup{\ref{def:shifted-rtt-boundary-quotient}},
and the corresponding cobar algebra coincides with the quantized
Coulomb branch of the rank-one $A_1$ theory.  The remaining rank-one
task is not homological algebra but the explicit identification of the
boundary parameter $c$ with the Coulomb-branch mass/FI data.
\end{conjecture}

\begin{remark}[Synthesis: the fortified Yangian frontier]
\label{rem:shifted-rtt-synthesis}
The results of this section separate the ordered Yangian programme
into exact pieces.  Positive weight towers admit stabilized completed
bar/cobar recovery
(Theorem~\ref{thm:shifted-rtt-stabilized-recovery}) and weightwise MC
descent (Theorem~\ref{thm:shifted-rtt-mc-descent}).  A finite
bar-duality datum yields the trace-theoretic chain isomorphism
$\Theta_A$ and a tangent-level Lagrangian envelope
(Theorem~\ref{thm:shifted-rtt-trace-duality},
Corollary~\ref{cor:shifted-rtt-lagrangian-envelope}).  The local
finite RTT kernel is self-dual under $R \mapsto R^{-1}$ by strict bar
adjointness (Theorem~\ref{thm:shifted-rtt-bar-adjointness}), and the
bi-diagonal twist transports this adjointness exactly
(Theorem~\ref{thm:shifted-rtt-shifted-bar-adjointness}).  The
genuinely new shifted datum lives in the boundary quotient, whose dual
is the orthogonal coideal
(Theorem~\ref{thm:shifted-rtt-coideal-descent}).  In the rank-one
case, this mechanism already produces the quantized Kleinian surface
$A_1$ (Theorem~\ref{thm:shifted-rtt-kleinian}).

The remaining work is sharply localized:
\begin{enumerate}[label=\textup{(\roman*)}]
\item construct the genuine boundary quotient
  $I_{\mu,\lambda}^{(N)}$ compatibly with the BFN and shifted-Yangian
  presentations;
\item identify the orthogonal coideal with the expected
  Coulomb-branch dual;
\item lift the rank-one model to higher finite stages and then to
  completed towers;
\item match the meromorphic coproduct with the line-operator
  coproduct of \cite{DNP25} on compact generators;
\item globalize the tangent-level Lagrangian envelope to a genuine
  shifted-symplectic deformation theory on the factorization side.
\end{enumerate}
\end{remark}
