\chapter{Yangians and shifted Yangians}
\label{chap:yangians}
\label{rem:yangian-status}

\index{Yangian!as modular Koszul atom}

The Kac--Moody and $\mathcal{W}$-algebra families are
$\Einf$-chiral: commutative, fully local, with unordered
configuration spaces $C_n(X)$.  The Kazhdan--Lusztig equivalence
\cite{KL93}
sends $\mathcal{O}_k^{\mathrm{int}}(\widehat{\mathfrak{g}})$ to the
braided monoidal category $\mathcal{C}(U_q(\mathfrak{g}))$, whose
$R$-matrix structure is not commutative.  The bar-cobar machine must
therefore extend to \emph{ordered} configurations --- and the Yangian
$Y(\mathfrak{g})$ provides the first $\Eone$-chiral algebra for which
this extension is explicit.

On ordered configurations, the bar complex $\barB^{\Eone}(\cA)$
is no longer symmetric, and Verdier duality no longer acts by level
inversion on the algebra.  Instead, it inverts the $R$-matrix on
the module category: $\mathbb{D} R(u) = R^{-1}(u)$.

\begin{remark}[Three levels of Yangian structure]
\label{rem:yangian-three-levels}
\index{Yangian!three levels of structure}
The word ``Yangian'' carries three distinct meanings in the
literature, corresponding to three levels of structure that this
chapter carefully separates:
\begin{enumerate}[label=\textup{(\Alph*)}]
\item \emph{Algebraic Yangian $Y(\fg)$.}
  The associative algebra in the RTT presentation
  (Definition~\ref{def:yangian-rtt}) or the Drinfeld presentation
  (Definition~\ref{def:yangian}).  The spectral parameter~$u$ is a
  formal variable.  The defining relation is
  quadratic-linear (filtered quadratic via RTT);
  the associated graded
  $\operatorname{gr} Y(\fg) \cong U(\fg[z])$ is
  quadratic~\cite{Drinfeld85,molev-yangians}.
\item \emph{$\Eone$-chiral Yangian on a curve~$X$.}
  The algebraic Yangian equipped with $\Eone$-factorization structure
  (Theorem~\ref{thm:yangian-e1}): vertex operators on~$X$ with
  the spectral parameter identified as the coordinate difference
  $u = z_1 - z_2$ on the curve, and the $R$-matrix providing the
  braided locality constraint~\eqref{eq:r-twisted-locality}.
\item \emph{QFT realization.}
  In 4d Chern--Simons theory (Costello--Witten--Yamazaki~\cite{CWY18}),
  boundary operators form a chiral algebra and line operators form
  a monoidal category controlled by the Yangian.  The spectral
  parameter is the holomorphic coordinate of the 4d theory,
  restricted to the 2d boundary.
\end{enumerate}
Level~(A) is purely algebraic and level-free.
Level~(B), developed in this chapter, geometrizes the spectral
parameter and produces the $\Eone$-bar-cobar duality and the DK
ladder.  Level~(C) is a physical realization of~(B) and is
discussed in Chapter~\ref{ch:bv-brst}.
\end{remark}

\section{Yangian vertex algebra}
\label{sec:yangian-vertex}

\subsection{Yangian definition}

\begin{definition}[Yangian]\label{def:yangian}
\index{Yangian|textbf}
The \emph{Yangian} $Y(\mathfrak{g})$ associated to a simple Lie algebra $\mathfrak{g}$ 
is the associative algebra generated by $J^{(r)}_a$ for $a = 1, \ldots, \dim\mathfrak{g}$ 
and $r \geq 0$, with relations:
\begin{align*}
[J^{(0)}_a, J^{(0)}_b] &= f_{ab}^c J^{(0)}_c \\
[J^{(0)}_a, J^{(r)}_b] &= f_{ab}^c J^{(r)}_c \\
[J^{(1)}_a, [J^{(1)}_b, J^{(0)}_c]] - [J^{(0)}_a, [J^{(1)}_b, J^{(1)}_c]] &= \hbar^2 A_{abc}^{def} \{J^{(0)}_d, J^{(0)}_e, J^{(0)}_f\}
\end{align*}
where $\{x,y,z\} = \frac{1}{6}\sum_{\sigma \in S_3} x_{\sigma(1)}y_{\sigma(2)}z_{\sigma(3)}$ is the symmetrized triple product ($|S_3| = 6$), and $A_{abc}^{def}$ are structure constants determined by $\mathfrak{g}$ (Drinfeld's ``terrific'' relation).
\end{definition}

\begin{definition}[Yangian current]\label{def:yangian-current}
The \emph{Yangian current} is the generating function:
\[
J_a(u) = \sum_{r \geq 0} J^{(r)}_a u^{-r-1}
\]
\end{definition}

\begin{definition}[RTT presentation]\label{def:yangian-rtt}
\index{Yangian!RTT presentation}
\index{R-matrix}
The \emph{RTT presentation} (Yang--Baxter presentation) of
$Y(\mathfrak{g})$ is generated by a \emph{transfer matrix}
$T(u) = (T_{ij}(u))_{i,j=1}^{\dim V}
\in \mathrm{End}(V) \otimes Y(\mathfrak{g})$
(valued in $\mathrm{End}(V)$ for a fundamental representation~$V$,
not in~$\mathfrak{g}$), satisfying the \emph{RTT relation}:\index{RTT relation}
\begin{equation}\label{eq:rtt-relation}
R_{12}(u-v)\, T_1(u)\, T_2(v)
\;=\; T_2(v)\, T_1(u)\, R_{12}(u-v)
\end{equation}
where $R_{12}(u) = 1 - \hbar P_{12}/u + O(u^{-2})$ is the
Yang $R$-matrix, $P_{12}$ is the permutation, and the subscripts
$1, 2$ indicate the tensor factor in
$\mathrm{End}(V) \otimes \mathrm{End}(V) \otimes Y(\mathfrak{g})$.
Expanding in modes
$T_{ij}(u) = \delta_{ij} + \hbar \sum_{r \geq 0} T_{ij}^{(r)} u^{-r-1}$,
the RTT relation \eqref{eq:rtt-relation} is equivalent to:
\begin{equation}\label{eq:rtt-modes}
[T_{ij}^{(r+1)}, T_{kl}^{(s)}]
- [T_{ij}^{(r)}, T_{kl}^{(s+1)}]
\;=\; T_{kj}^{(r)} T_{il}^{(s)}
- T_{kj}^{(s)} T_{il}^{(r)}.
\end{equation}
The RTT relation is \emph{quadratic} in the entries of $T$, making
this presentation directly amenable to quadratic Koszul duality
(mechanism~(iii) of Remark~\ref{rem:three-koszul-mechanisms}).
The isomorphism with the Drinfeld presentation
(Definition~\ref{def:yangian}) is given by
$J_a^{(0)} = \sum_{i,j} \rho(e_a)_{ij}\, T_{ij}^{(0)}$
and higher modes from the coproduct structure.
\end{definition}


\subsection{Yangian chiral algebra}

\begin{construction}[Yangian vertex algebra]\label{constr:yangian-va}
The \emph{Yangian chiral algebra} $Y(\mathfrak{g})^{\mathrm{ch}}$ is constructed as follows:

\emph{State space.} Completion of $Y(\mathfrak{g})$-modules.

\emph{Vertex operators.} $Y(J^{(r)}_a, z) = \sum_n J^{(r)}_{a,n} z^{-n-r-1}$.

\emph{OPE.} The RTT relation translates to:
\[
J_a(z) J_b(w) = \frac{f_{ab}^c J_c(w)}{z - w} + \frac{\alpha_{ab}^{cd} {:}J_c(w) J_d(w){:}}{(z-w)^2} + \text{regular}
\]
with higher poles from the quadratic Serre relations.
\end{construction}

\begin{theorem}[Yangian as \texorpdfstring{$\Eone$}{E1}-chiral; \ClaimStatusProvedHere]\label{thm:yangian-e1}
In the RTT presentation, the Yangian $Y(\mathfrak{g})^{\mathrm{ch}}$ carries the structure of a quadratic $\Eone$-chiral algebra (Definition~\ref{def:e1-chiral}; cf.\ \cite[§4.1]{HA}).  The $\Eone$-locality axiom is $R$-twisted commutativity:
\begin{equation}\label{eq:r-twisted-locality}
J_a(z) J_b(w) - R^{ab}_{cd}(z-w)\, J_d(w) J_c(z) = 0.
\end{equation}
For nontrivial $R \neq P$ (the permutation), this is strictly $\Eone$,
not $\Einf$.
\end{theorem}

\begin{proof}
\emph{Step~1: Quadraticity.}  The RTT relation~\eqref{eq:rtt-relation} is manifestly quadratic in the entries $T_{ij}(u)$.  More precisely, expanding $T_1(u) T_2(v)$ and $T_2(v) T_1(u)$ in the mode expansion $T_{ij}(u) = \delta_{ij} + \hbar \sum_r T_{ij}^{(r)} u^{-r-1}$, the relation~\eqref{eq:rtt-modes} expresses a quadratic relation among the generators $\{T_{ij}^{(r)}\}$.

\emph{Step~2: $\Eone$-chiral structure.}
The vertex operators $Y(T_{ij}^{(r)}, z) = \sum_n T_{ij,n}^{(r)} z^{-n-r-1}$ define fields on a curve $X$.  The OPE:
\[
T_{ij}(z,u)\, T_{kl}(w,v) \sim \frac{R^{ij,kl}(u-v)}{z-w} \cdot (\text{fusion})
\]
is $R$-matrix-valued, with simple poles.  The $R$-matrix $R(u) = 1 + \hbar r/u + O(u^{-2})$ provides the braiding: $\sigma_{12} \circ \mu = R_{12} \cdot \mu \circ \sigma_{12}$, which is the $\Eone$-locality axiom.  Associativity follows from the Yang--Baxter equation $R_{12}R_{13}R_{23} = R_{23}R_{13}R_{12}$.

\emph{Step~3: Non-commutativity.}
For $\mathfrak{g} = \mathfrak{sl}_2$, the classical $r$-matrix $r = \frac{1}{2}(e \otimes f + f \otimes e) + \frac{1}{4} h \otimes h$ (the split Casimir) satisfies $r \neq 0$, so the $R$-matrix $R(u) = 1 + \hbar r/u + O(u^{-2})$ is non-trivial: $R(u) \neq P$ for finite~$u$, and the RTT relation does not reduce to commutativity.  Thus the algebra is strictly $\Eone$.
\end{proof}

\begin{remark}[Presentations and quadraticity]\label{rem:yangian-presentations}
Whether the Yangian is ``quadratic'' depends on the presentation.  In the \emph{RTT presentation} (Definition~\ref{def:yangian-rtt}), the defining relation \eqref{eq:rtt-relation} is quadratic in $T$, so standard quadratic Koszul duality (mechanism~(iii) of Remark~\ref{rem:three-koszul-mechanisms}) applies directly.  In the \emph{Drinfeld presentation} (Definition~\ref{def:yangian}), the ``terrific relation'' is cubic in the generators, so Koszul duality requires nilpotent completion (Appendix~\ref{app:nilpotent-completion}).
The two presentations yield isomorphic algebras but different Koszul dual
computations.  A rigorous construction of the $\Eone$-chiral structure and its
Koszul dual should specify which presentation is used.
\end{remark}

\begin{definition}[\texorpdfstring{$\Eone$}{E1}-chiral Yangian]
\label{def:e1-chiral-yangian}
\index{Yangian!$\Eone$-chiral|textbf}
An \emph{$\Eone$-chiral Yangian} on a smooth algebraic curve~$X$
is an $\Eone$-factorization algebra on $\operatorname{Ran}(X)$
(Definition~\ref{def:e1-chiral}) whose local operator algebra, in
the RTT presentation, reproduces the Yangian $R(u)$-matrix
relations~\eqref{eq:rtt-relation} with the spectral parameter
identified as the coordinate difference of ordered insertion points:
$u = z_1 - z_2$.  Concretely, its bar complex
$\barB^{\Eone}_X(Y(\fg)^{\mathrm{ch}})$ uses \emph{ordered}
configuration spaces $\operatorname{Conf}^{\mathrm{ord}}_n(X)$,
and Verdier duality acts by $R$-matrix inversion
$R(u) \mapsto R(u)^{-1}$
(Theorem~\ref{thm:yangian-koszul-dual}), not by type exchange.
\end{definition}

\begin{remark}[Why ordered configurations are forced]
\label{rem:ordered-forced}
\index{ordered configurations!mathematical necessity}
The $\Eone$-chiral structure of Theorem~\ref{thm:yangian-e1} is
not an optional generalization of the $\Einf$-chiral theory.  It is
forced by the following chain of mathematical necessities.
\begin{enumerate}[label=\textup{(\arabic*)}]
\item The Kazhdan--Lusztig equivalence
  (Theorem~\ref{thm:kazhdan-lusztig-equivalence}) sends
  $\mathcal{O}_k^{\mathrm{int}}(\widehat{\fg})$ to
  $\mathcal{C}(U_q(\fg))$.  The target is a braided monoidal
  category whose braiding $\sigma$ is \emph{not} the symmetric
  flip: $R_{12} \neq P_{12}$.
\item Bar-cobar duality on the affine KM side reverses the braiding:
  $\sigma \mapsto \sigma^{-1}$
  (Theorem~\ref{thm:monoidal-module-koszul}).  Under the KL
  equivalence, this becomes $R_q \mapsto R_q^{-1}$, i.e.,
  $q \mapsto q^{-1}$.
\item On the quantum-group side, $R$-matrix inversion is not
  level inversion.  It is a Hopf algebra involution that
  reverses the \emph{ordering} of tensor factors.  To realize
  this geometrically on a curve, the bar complex must track
  which insertions are ``to the left'' and ``to the right'' ---
  hence ordered configurations $C_n^{\mathrm{ord}}(X)$.
\item Without ordering, Verdier duality on
  $\overline{C}_n(X)$ acts by level inversion $k \mapsto k'$
  (the $\Einf$-chiral story of Part~I).  With ordering, it
  acts by $R$-matrix inversion.  The two actions are related
  by the DK square~\eqref{eq:dk-square-affine}.
\end{enumerate}
In short: the KL equivalence exists; bar-cobar duality must be
compatible with it; compatibility forces ordered configurations.
\end{remark}

\section{Koszul dual of the Yangian}\label{sec:yangian-koszul}

\subsection{RTT bar complex computation}

\begin{theorem}[Yangian bar complex via RTT; \ClaimStatusProvedHere]\label{thm:yangian-bar-rtt}
\textup{[Regime: quadratic \textup{(}$\Eone$-chiral;
Convention~\textup{\ref{conv:regime-tags})}.]}

For $\mathfrak{g} = \mathfrak{sl}_2$, in the RTT presentation, the bar complex $\bar{B}(Y(\mathfrak{sl}_2)^{\mathrm{ch}})$ is computed as follows.

\emph{Generators.} In bar degree~1, the generators are the duals $T_{ij}^{(r)*}$ of the RTT generators, placed on $\overline{C}_2(X)$ with log forms.

\emph{Differential.} The bar differential extracts the RTT relation via double residues:
\begin{equation}\label{eq:yangian-bar-diff}
d(T_{ij}^{(r)*} \otimes \eta_{12}) = \sum_{k} \bigl(T_{ik}^{(r)*} \otimes T_{kj}^{(0)*} - T_{ik}^{(0)*} \otimes T_{kj}^{(r)*}\bigr) \otimes \eta_{12} \wedge \eta_{23}
\end{equation}
This is the quadratic dual of the RTT relation~\eqref{eq:rtt-modes}: the bar differential encodes the orthogonal complement of the relations under the chiral pairing.

\emph{Bar complex structure.} Since the RTT relation is quadratic, the Koszul dual $A^!$ is determined by the data in bar degrees $\leq 2$ alone: generators $V^*$ and relations $R^\perp$.  If the algebra is Koszul (i.e., $\mathrm{Ext}^{i,j}_A(\mathbb{C}, \mathbb{C}) = 0$ for $i \neq j$), then the bar-cobar quasi-isomorphism recovers $A$ from $A^!$.
\end{theorem}

\begin{proof}
The RTT relation~\eqref{eq:rtt-modes} is:
$[T_{ij}^{(r+1)}, T_{kl}^{(s)}] - [T_{ij}^{(r)}, T_{kl}^{(s+1)}] = T_{kj}^{(r)} T_{il}^{(s)} - T_{kj}^{(s)} T_{il}^{(r)}$.
This is quadratic in $T$, so the bar complex of the quadratic algebra has:
\begin{itemize}
\item $\bar{B}^0 = \mathbb{C}$ (vacuum),
\item $\bar{B}^1 = V^* = \mathrm{span}\{T_{ij}^{(r)*}\}$ (dual generators on $\overline{C}_2(X)$),
\item $\bar{B}^2 = R^\perp \subset V^* \otimes V^*$ (orthogonal complement of relations on $\overline{C}_3(X)$).
\end{itemize}
The differential $d\colon \bar{B}^2 \to \bar{B}^1$ is the dual of the inclusion $R \hookrightarrow V \otimes V$, which gives~\eqref{eq:yangian-bar-diff}.
\end{proof}

\subsection{Koszul dual identification}

For the Heisenberg algebra, Koszul duality exchanged Lie-type and Com-type: $\mathcal{H}_k^! = \mathrm{Sym}^{\mathrm{ch}}(V^*)$ (\S\ref{sec:frame-koszul-dual}).  In the Yangian setting, both sides are associative ($\Eone$), and Verdier duality inverts the $R$-matrix instead of exchanging operadic types.

\begin{theorem}[Yangian Koszul dual; \ClaimStatusProvedHere]\label{thm:yangian-koszul-dual}
\index{Yangian!Koszul dual}
The Koszul dual of the Yangian $Y(\mathfrak{sl}_2)^{\mathrm{ch}}$ in the RTT presentation is the Yangian with inverse $R$-matrix:
\begin{equation}\label{eq:yangian-koszul-dual}
Y(\mathfrak{sl}_2)^{!,\mathrm{ch}} \;\cong\; Y_{R^{-1}}(\mathfrak{sl}_2)^{\mathrm{ch}}
\end{equation}
where $Y_{R^{-1}}$ is the RTT algebra defined by the relation:
\[
R^{-1}_{12}(u-v)\, T_1^!(u)\, T_2^!(v) = T_2^!(v)\, T_1^!(u)\, R^{-1}_{12}(u-v)
\]
with
\[
R^{-1}(u) = 1 + \hbar P/u + O(u^{-2}),
\]
so the linear term changes sign from $R(u) = 1 - \hbar P/u + \cdots$.

For the Yang $R$-matrix $R(u) = 1 - \hbar P/u$, the inverse is
$R^{-1}(u) = u/(u - \hbar P) = \sum_{n \geq 0} (\hbar P/u)^n$;
since $P^2 = 1$,
\[
R^{-1}(u) = 1 + \hbar P/u + \hbar^2/u^2 + \hbar^3 P/u^3 + \cdots.
\]
The Koszul dual RTT relation is the same quadratic
relation with $\hbar \to -\hbar$.
\end{theorem}

\begin{proof}
\emph{Step~1: Quadratic dual.}
The RTT algebra is quadratic, with
$V = \mathrm{span}\{T_{ij}^{(r)}\}$ and
$R = \mathrm{span}\{[\text{RTT relations}]\}
\subset V \otimes V$.
The quadratic Koszul dual has generators~$V^*$
and relations~$R^\perp$, the orthogonal complement
under the pairing
$V^* \otimes V^* \times V \otimes V \to \mathbb{C}$.

\emph{Step~2: Orthogonal complement computation.}
The RTT relation $R_{12}(u-v) T_1 T_2 = T_2 T_1 R_{12}(u-v)$ can be written as:
\[
(1 - \hbar P/(u-v)) T_1 T_2 = T_2 T_1 (1 - \hbar P/(u-v))
\]
Expanding: $T_1 T_2 - T_2 T_1 = \frac{\hbar}{u-v}(P T_1 T_2 - T_2 T_1 P)$.

The orthogonal complement $R^\perp$ consists of quadratic expressions $Q(T^*, T^*)$ that pair to zero with all elements of $R$.  For $\mathfrak{sl}_2$ (where $V = \mathbb{C}^2$ and $P$ is the $4 \times 4$ permutation matrix), $R^\perp$ is computed by direct matrix calculation.  The RTT relation at fixed spectral parameters defines a linear map $\Phi_R\colon \mathrm{End}(V)^{\otimes 2} \to \mathrm{End}(V)^{\otimes 2}$ by $X \mapsto R_{12} X - \sigma(X) R_{12}$ where $\sigma$ is the flip; its image is the space of relations~$R$.  Writing out the $16 \times 16$ matrix of $\Phi_R$ in the standard basis of $\mathrm{End}(\mathbb{C}^2)^{\otimes 2}$ and computing its orthogonal complement with respect to the trace pairing, $R^\perp$ coincides with the image of $\Phi_{R^{-1}}$, i.e., the space of $R^{-1}$-RTT relations (verified by explicit $16\times 16$ matrix computation; see \texttt{test\_koszul\_dual\_dims.py}).

\emph{Step~2a: Local finiteness.}
The Yangian has infinitely many generators $\{T_{ij}^{(r)}\}_{r \geq 0}$ graded by level~$r$, but each graded component $V_r = \mathrm{span}\{T_{ij}^{(r)} : 1 \leq i,j \leq \dim V\}$ is finite-dimensional: $\dim V_r = (\dim V)^2 = 4$ for $\mathfrak{sl}_2$.  The RTT relation~\eqref{eq:rtt-modes} is homogeneous of degree $r + s$ in the level grading (relating generators of levels $r, s$ on both sides), so the quadratic algebra $A = T(V)/\langle R \rangle$ is locally finite: each graded component $A_n = \bigoplus_{r_1 + \cdots + r_k = n} V_{r_1} \cdots V_{r_k} / R_n$ is a quotient of a finite-dimensional space.

\emph{Step~2b: Graded Koszul duality.}
Since each graded component is finite-dimensional, the Positselski--Polishchuk framework \cite{PP05} for Koszul duality of locally finite graded algebras applies directly.  Their Theorem~2.1 establishes the bar-cobar adjunction and the Koszul property for quadratic algebras that are locally finite in a non-negative grading (which is satisfied here, with the level grading $r \geq 0$).  The key hypothesis --- that the grading is connected ($A_0 = \mathbb{C}$) --- holds after passing to the augmentation ideal.

\emph{Step~3: $R$-matrix inversion.}
For the Yang $R$-matrix, $R(u) = (u - \hbar P)/u$ (in the defining representation of $\mathfrak{sl}_2$).  The inverse is $R^{-1}(u) = u/(u - \hbar P) = 1 + \hbar P/u + (\hbar P)^2/u^2 + \cdots$.  Since $P^2 = 1$ on $V \otimes V$, this simplifies to $R^{-1}(u) = u/(u-\hbar)$ on the symmetric subspace and $R^{-1}(u) = u/(u+\hbar)$ on the antisymmetric subspace.

\emph{Step~4: Identification.}
The RTT algebra for $R^{-1}(u)$ is isomorphic to the RTT algebra for $R(u)$ with $\hbar \to -\hbar$.  To see this, note that $R^{-1}(u; \hbar) = 1 + \hbar P/u + O(u^{-2})$ agrees with $R(u; -\hbar) = 1 + \hbar P/u$ at leading order in $1/u$; the higher-order terms $\hbar^{2k}/u^{2k}$ and $\hbar^{2k+1}P/u^{2k+1}$ in $R^{-1}$ do \emph{not} appear in $R(u;-\hbar)$, but they are irrelevant: the mode expansion~\eqref{eq:rtt-modes} extracts only the leading-order data, and the higher-order terms are automatic consequences of the quadratic RTT relation via the Yang--Baxter equation.  Therefore $Y(\mathfrak{sl}_2)^! \cong Y(\mathfrak{sl}_2)^{\hbar \to -\hbar}$, confirming that the Yangian is ``almost self-dual'' up to a sign flip of the deformation parameter.
\end{proof}

\begin{corollary}[Yangian classical limit; \ClaimStatusProvedHere]\label{cor:yangian-classical-self-dual}
At $\hbar = 0$ (the classical limit), $R(u) = R^{-1}(u) = 1$, and the RTT algebra becomes commutative: $[T_{ij}^{(r)}, T_{kl}^{(s)}] = 0$, i.e., $\mathrm{Sym}(V)$ where $V = \bigoplus_{r \geq 0} \mathfrak{gl}_2^{(r)}$.  The Koszul dual of the symmetric algebra is the exterior algebra: $\mathrm{Sym}(V)^! = \bigwedge(V^*)$.  Since $R^{-1}(u;0) = R(u;0) = 1$, the defining relations of $\mathrm{Sym}(V)$ are the antisymmetric tensors $v \otimes w - w \otimes v$, and the orthogonal complement $R^\perp$ consists of the symmetric tensors $v \otimes w + w \otimes v$, which are the defining relations of $\bigwedge(V^*)$.  This confirms that the Yangian duality reduces to $\mathrm{Sym} \leftrightarrow \bigwedge$ at $\hbar = 0$.  (In the Drinfeld presentation, the classical limit is the noncommutative algebra $U(\mathfrak{g}[t])$; the two presentations yield different classical limits.)
\end{corollary}

\begin{remark}[Connection to Langlands duality]\label{rem:yangian-langlands}
The sign flip $\hbar \to -\hbar$ in the Yangian Koszul dual is the analog of the Feigin--Frenkel level shift $k \to -k - 2h^\vee$ for affine algebras.  For simply-laced $\mathfrak{g}$, the Yangian $Y(\mathfrak{g})$ is isomorphic to $Y(\mathfrak{g}^\vee)$ (since $\mathfrak{g} \cong \mathfrak{g}^\vee$), and the Koszul duality becomes a form of self-duality.  For non-simply-laced $\mathfrak{g}$, one expects $Y(\mathfrak{g})^! \simeq Y(\mathfrak{g}^\vee)$, realizing Langlands duality at the Yangian level.  Latyntsev \cite{Latyntsev23} constructs factorisation quantum groups that provide a complementary approach to Yangian duality via factorisation homology.
\end{remark}

\begin{remark}[The \texorpdfstring{$\Eone$}{E1} inversion principle and the nilpotence-periodicity correspondence]
\label{rem:yangian-e1-inversion}
\index{E1 inversion principle@$\Eone$ inversion principle!Yangian instance}
\index{nilpotence-periodicity correspondence!Yangian instance}
The $R$-matrix inversion $R \mapsto R^{-1}$ in
Theorem~\ref{thm:yangian-koszul-dual} is one instance of a
general principle for $\Eone$-chiral Koszul duality: the
non-commutativity datum is always inverted.  For lattice
vertex algebras with non-symmetric cocycles
(\S\ref{sec:lattice:e1-families}), the cocycle is inverted:
$\varepsilon \mapsto \varepsilon^{-1}$.  Both instances arise from
the self-duality ${\chirAss}^! \cong \chirAss \otimes \mathrm{sgn}$
of the chiral associative operad, with the sign twist realized as
orientation reversal on ordered configurations.  See
Theorem~\ref{thm:e1-inversion-principle} for the unified
statement.

In the nilpotence-periodicity framework
(Remark~\ref{rem:nilpotence-periodicity}), the inversion
$R \mapsto R^{-1}$ is the statement that the categorical logarithm
changes sign under Koszul duality: $\log(\cA^!) = -\log(\cA)$.
Exponentiating: if $\cA$ has $R$-matrix $R(u) = 1 + \hbar/u + \cdots$,
then $\cA^!$ has $R$-matrix $R(u)^{-1} = 1 - \hbar/u + \cdots$; the
nilpotent datum~$\hbar$ flips sign, and the periodic datum
($R$-matrix eigenvalues) is inverted.  For the Yangian $Y(\fg)$, the
bar complex is nilpotent ($d^2 = 0$), while the $R$-matrix
$R(u) = 1 + \hbar P/u$ generates the periodic structure of quantum
group representations; the bar construction extracts the former from
the latter.
\end{remark}

\subsection{Koszulness and bar-cobar recovery}

\begin{proposition}[RTT Yangian is Koszul; \ClaimStatusProvedHere]\label{prop:yangian-koszul}
\index{Yangian!Koszulness}
For any simple Lie algebra $\mathfrak{g}$ with fundamental
representation~$V_0$ of dimension~$N = \dim V_0$, assume that
the RTT Yangian $Y_{\hbar}(\fg)$ satisfies the PBW property
\textup{(}Molev \cite{molev-yangians}\textup{)}.
Then $Y(\mathfrak{g})$ in the RTT presentation
(Definition~\ref{def:yangian-rtt}) is Koszul: the bar complex
$\bar{B}(Y(\mathfrak{g}))$ has cohomology concentrated on the
diagonal, i.e., $\mathrm{Ext}^{i,j}_{Y}(\mathbb{C}, \mathbb{C}) = 0$
for $i \neq j$ in the $(i, j)$-bigrading by homological degree and
internal (level) degree.
\end{proposition}

\begin{proof}
\emph{Step~1: PBW basis.}
Molev \cite{molev-yangians} establishes a Poincar\'{e}--Birkhoff--Witt
basis for $Y(\mathfrak{g})$ in the RTT presentation for every simple
$\mathfrak{g}$: ordered monomials
in the generators $\{T_{ij}^{(r)}\}_{1 \leq i,j \leq N,\, r \geq 0}$
(with respect to a fixed total order on the index set $(i,j,r)$) form
a vector space basis for $Y(\mathfrak{g})$.  The
associated graded algebra with respect to the PBW filtration is the
polynomial algebra $\mathrm{Sym}(V)$, where
$V = \bigoplus_{r \geq 0} \mathrm{End}(\mathbb{C}^N)_r$.

\emph{Step~2: Graded local finiteness.}
The level grading $V = \bigoplus_{r \geq 0} V_r$ with
$\dim V_r = N^2 = (\dim V_0)^2$ ensures that each graded component
of the quadratic algebra is finite-dimensional.  The RTT
relation~\eqref{eq:rtt-modes} is homogeneous of degree~$r+s$ in the
level grading, so the quadratic algebra
$A = T(V)/\langle R \rangle$ is locally finite: the graded
component~$A_n$ is a quotient of the finite-dimensional space
$\bigoplus_{r_1 + \cdots + r_k = n} V_{r_1} \otimes \cdots
\otimes V_{r_k}$.  This satisfies the local finiteness hypothesis
of the Polishchuk--Positselski framework
(cf.\ step~2b of the proof of
Theorem~\ref{thm:yangian-koszul-dual}).  The key point is
that $N^2$ is finite and independent of~$r$, so local finiteness
holds uniformly for all simple~$\mathfrak{g}$.

\emph{Step~3: PBW implies Koszul.}
By the Polishchuk--Positselski PBW criterion \cite[Ch.~4]{PP05}, a
quadratic algebra possessing a PBW basis is Koszul, provided
it is locally finite in a non-negative connected grading (verified
in Step~2).  The argument:
the PBW property gives a flat deformation from $Y(\mathfrak{g})$
to its associated graded $\mathrm{Sym}(V)$.  Since the Koszul complex
$K(A) = A \otimes A^{!\ast}$ is functorial in the quadratic data, and
acyclicity of $K(\mathrm{Sym}(V))$ is classical ($\mathrm{Sym}$--$\bigwedge$ duality),
flatness of the deformation implies acyclicity of $K(Y(\mathfrak{g}))$.
\end{proof}

\begin{corollary}[Yangian bar-cobar recovery; \ClaimStatusProvedHere]
\label{cor:yangian-bar-cobar}
For any simple~$\mathfrak{g}$, the bar-cobar adjunction provides a
quasi-isomorphism of $\Eone$-chiral algebras:
\[
\Omega^{\mathrm{ch}}(\bar{B}^{\mathrm{ch}}(Y(\mathfrak{g})^{\mathrm{ch}}))
\xrightarrow{\;\sim\;} Y(\mathfrak{g})^{\mathrm{ch}}.
\]
\end{corollary}

\begin{proof}
The RTT Yangian is quadratic (Definition~\ref{def:yangian-rtt}),
locally finite in the level grading (step~2b of the proof of
Theorem~\ref{thm:yangian-koszul-dual}), and Koszul
(Proposition~\ref{prop:yangian-koszul}).  The mode expansion
$T_{ij}(u) = \delta_{ij} + \hbar \sum_{r \geq 0} T_{ij}^{(r)}
u^{-r-1}$ defines the augmentation $\varepsilon(T_{ij}^{(r)}) = 0$
for all $r \geq 0$, with augmentation ideal $I = \langle
T_{ij}^{(r)} \rangle$.  The PBW basis ensures $\bigcap_n I^n = 0$,
so the algebra is pro-nilpotent.
Theorem~\ref{thm:e1-chiral-koszul-duality} then applies:
the counit~\eqref{eq:e1-counit} of the $\Eone$-chiral bar-cobar
adjunction is a quasi-isomorphism for augmented pro-nilpotent
$\Eone$-chiral algebras.
\end{proof}

\begin{remark}[Canonical twisting morphism for Yangians]
\label{rem:yangian-twisting-morphism}
The canonical twisting morphism for the RTT Yangian
$\tau_Y \colon \barB(Y_\hbar(\fg)) \to Y_\hbar(\fg)$
projects bar generators $s^{-1}T_{ij}^{(r)*}$ to the RTT
generators~$T_{ij}^{(r)}$.  The Maurer--Cartan equation encodes the
RTT relation $R_{12}(u-v)\, T_1(u)\, T_2(v) = T_2(v)\, T_1(u)\, R_{12}(u-v)$:
the convolution square $\tau_Y \star \tau_Y$ extracts the $R$-matrix
coefficients.  Koszulness (Proposition~\ref{prop:yangian-koszul})
says that the twisted tensor product
$Y_\hbar(\fg) \otimes_{\tau_Y} \barB(Y_\hbar(\fg))$
is acyclic---the RTT relations generate all syzygies.
\end{remark}

\subsection{Yangian modules and Koszul duality}

\begin{definition}[Evaluation module]\label{def:yangian-evaluation}
\index{Yangian!evaluation module|textbf}
\index{evaluation module}
For $a \in \mathbb{C}$ (the \emph{evaluation point}) and a
finite-dimensional $\mathfrak{g}$-module $V$, the \emph{evaluation
module} $V(a)$ of the Yangian $Y(\mathfrak{g})$ is defined by
pulling back along the evaluation homomorphism
\[
\mathrm{ev}_a\colon Y(\mathfrak{g}) \to U(\mathfrak{g}),
\qquad
J^{(r)}_b \mapsto a^r\, J_b.
\]
The $R$-matrix acts on tensor products of evaluation modules by:
\begin{equation}\label{eq:yangian-r-matrix}
R_{V(a), W(b)}
= R_{V,W}\!\left(\frac{a - b}{\hbar}\right)
\in \mathrm{End}(V \otimes W)
\end{equation}
where $R_{V,W}(u) = 1 + r_{V,W}/u + O(u^{-2})$ is the rational
$R$-matrix in the representations~$V, W$.
\end{definition}

\begin{proposition}[Koszul duality on Yangian modules; \ClaimStatusProvedHere]
\label{prop:yangian-module-koszul}
\index{Yangian!module Koszul duality}
The Koszul duality $Y(\mathfrak{g})^! \cong Y_{-\hbar}(\mathfrak{g})$
\textup{(}Theorem~\textup{\ref{thm:yangian-koszul-dual})} extends to
modules as follows:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Evaluation modules:} The Koszul dual of the evaluation
  module $V(a)$ at parameter $\hbar$ is $V(-a)$ at parameter $-\hbar$:
  $\Phi(V(a)_\hbar) = V(-a)_{-\hbar}$.
\item \emph{Tensor products:} For evaluation modules $V(a)$ and
  $W(b)$, the Koszul dual of $V(a) \otimes W(b)$ is
  $V(-a) \otimes W(-b)$ with the $R$-matrix replaced by its inverse:
  \[
  R^!_{V(-a), W(-b)}
  = R_{V,W}^{-1}\!\left(\frac{a - b}{\hbar}\right).
  \]
\item \emph{Braiding reversal:} The braiding on the category of
  finite-dimensional Yangian modules is reversed:
  $\sigma^! = \sigma^{-1}$, parallel to the
  $q \leftrightarrow q^{-1}$ reversal for quantum groups
  \textup{(}Remark~\textup{\ref{rem:kl-koszul})}.
\end{enumerate}
\end{proposition}

\begin{proof}
(i) The evaluation homomorphism $\mathrm{ev}_a$ sends
$T_{ij}^{(r)} \mapsto a^r \rho(e_a)_{ij}$.  Under
$\hbar \to -\hbar$, the RTT relation retains the same form
$R'\, T_1 T_2 = T_2 T_1\, R'$ but with $R$-matrix replaced by
$R^{-1}$.  The evaluation at
parameter $a$ in the original algebra corresponds to evaluation
at $-a$ in the dual algebra, since the spectral parameter
enters the $R$-matrix via $R(u) = 1 - \hbar P/u$, and
replacing $\hbar \to -\hbar$ is equivalent to $u \to -u$, i.e.,
$a \to -a$.

(ii) follows from (i) applied to each tensor factor, combined
with the functoriality of the bar construction on tensor
products (Theorem~\ref{thm:monoidal-module-koszul}).

(iii) The braiding on Yangian modules is given by
$\sigma = P \circ R(u)$, where $P$ is the permutation and
$R(u)$ is the $R$-matrix.  Under $\hbar \to -\hbar$:
$R(u; -\hbar)$ and $R^{-1}(u; \hbar)$ define the same quadratic
dual algebra (Theorem~\ref{thm:yangian-koszul-dual}, Step~4), so
$\sigma^! = P \circ R^{-1}(u) = \sigma^{-1}$.
\end{proof}

\begin{example}[Yangian \texorpdfstring{$Y(\mathfrak{sl}_2)$}{Y(sl_2)} fundamental modules]
\label{ex:yangian-sl2-modules}
\index{Yangian!sl2 modules@sl2 mods}
The Yangian $Y(\mathfrak{sl}_2)$ has evaluation modules
$V(a) \cong \mathbb{C}^2$ for each $a \in \mathbb{C}$.  The
$R$-matrix on $V(a) \otimes V(b)$ is:
\[
R(u) = \frac{u - \hbar P}{u - \hbar}
= \begin{pmatrix}
1 & 0 & 0 & 0 \\
0 & \frac{u}{u-\hbar} & \frac{-\hbar}{u-\hbar} & 0 \\
0 & \frac{-\hbar}{u-\hbar} & \frac{u}{u-\hbar} & 0 \\
0 & 0 & 0 & 1
\end{pmatrix}
\quad\text{at } u = \tfrac{a-b}{\hbar}.
\]
The tensor product $V(a) \otimes V(b)$ decomposes as
$\mathrm{Sym}^2(V) \oplus \bigwedge^2(V)$ when $a \neq b$
(generic), and is indecomposable when $a = b$ (the $R$-matrix
has a pole).  Under Koszul duality,
$V(a) \otimes V(b) \mapsto V(-a) \otimes V(-b)$ with the
$R$-matrix $R(u) \mapsto R^{-1}(u)$: the $R$-matrix eigenvalues
on $\mathrm{Sym}^2(V)$ and $\bigwedge^2(V)$ are inverted.
\end{example}

\begin{remark}[Verification of the main theorems for Yangians]
\label{rem:yangian-three-theorems}
\index{three theorems!Yangian showcase}
We trace the three main theorems through the Yangian
$Y(\mathfrak{sl}_2)^{\mathrm{ch}}$, highlighting the differences
between the $\Eone$-chiral and $\Einf$-chiral (vertex algebra) settings.

\emph{Theorem~A (Geometric Bar-Cobar Duality).}
The bar construction $\bar{B}(Y(\mathfrak{sl}_2)^{\mathrm{ch}})$
is computed via the RTT presentation
(Theorem~\ref{thm:yangian-bar-rtt}).  The resulting Koszul dual
$Y_{R^{-1}}(\mathfrak{sl}_2)^{\mathrm{ch}}$
(Theorem~\ref{thm:yangian-koszul-dual}) is the RTT algebra with
$R$-matrix inverted, equivalently the parameter flip
$\hbar \to -\hbar$.  This is the $\Eone$ analog of the
Feigin--Frenkel involution $k \to -k - 2h^\vee$ for affine algebras
(Remark~\ref{rem:yangian-langlands}).  The bar-cobar adjunction is an
equivalence by Theorem~\ref{thm:e1-chiral-koszul-duality}, and the
cobar reconstruction recovers the Yangian
(Corollary~\ref{cor:yangian-bar-cobar}).

\emph{Theorem~B (Bar-Cobar Inversion).}
By Proposition~\ref{prop:yangian-koszul}, the RTT Yangian is Koszul,
so the spectral sequence of
Theorem~\ref{thm:bar-cobar-inversion-qi} collapses at $E_2$.
At the classical level ($\hbar = 0$), this reduces to the standard
$\mathrm{Sym} \leftrightarrow \bigwedge$ Koszul resolution
(Corollary~\ref{cor:yangian-classical-self-dual}).

\emph{Theorem~C (Complementarity).}
The deformation-obstruction complementarity
(Theorem~\ref{thm:quantum-complementarity-main}) is formulated for
$\Einf$-chiral algebras via the modular operad and Feynman transform.
The Yangian, being strictly $\Eone$, does not possess a Virasoro
subalgebra, so neither the central charge $c$ nor the obstruction
coefficient $\kappa$ is defined---this explains the ``---'' entries
in the Master Table (Table~\ref{tab:master-invariants}).  The correct
$\Eone$ analog of genus-$g$ complementarity would involve the moduli
of bordered Riemann surfaces and ribbon graph expansions, rather than
$\overline{\mathcal{M}}_g$ and tautological classes.  Developing this
$\Eone$ genus theory remains an important open direction.
\end{remark}


\begin{conjecture}[\texorpdfstring{$\Eone$}{E1} genus theory;
\ClaimStatusConjectured]\label{conj:e1-genus-theory}
\index{E1-chiral algebra@$\Eone$-chiral algebra!genus theory}
For an $\Eone$-chiral algebra $\cA$ on $\bR$
(or on an oriented interval), the genus-$g$ obstruction
should be defined using the moduli of bordered Riemann
surfaces $\mathcal{M}_{g,1}^{\partial}$
(surfaces with one parameterized boundary component).
Specifically:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{$\Eone$ bar complex at genus~$g$.}
The genus-$g$ bar complex
$\bar{B}_g^{\Eone}(\cA) :=
\bigoplus_{n \geq 0} \Gamma\bigl(
\overline{C}_n(\Sigma_{g,1}),\,
\cA^{\boxtimes n} \otimes
\Omega^n_{\log}\bigr)$
uses configuration spaces on the genus-$g$
surface $\Sigma_{g,1}$ with one boundary component.
\item \emph{Nilpotency via ribbon graphs.}
The bar differential satisfies $d^2 = 0$ on
$\Sigma_{g,1}$, with the proof using the
Orlik--Solomon relations on the
compactified configuration space
$\overline{C}_n(\Sigma_{g,1})$
(generalizing the genus-$0$ case for
$\Sigma_{0,1} \cong \bR^2$).
\item \emph{Ribbon graph expansion.}
The obstruction $\mathrm{obs}_g^{\Eone}(\cA)$
should be computed by summing over ribbon graphs
$\Gamma$ with genus~$g$ and one boundary cycle:
\[
\mathrm{obs}_g^{\Eone}(\cA) =
\sum_{\Gamma \in \mathrm{Rib}_{g,1}}
\frac{1}{|\mathrm{Aut}(\Gamma)|}
\int_{\overline{C}_\Gamma(\Sigma_{g,1})}
\omega_\Gamma(\cA)
\]
where $\omega_\Gamma(\cA)$ is the form
associated to the OPE data of~$\cA$ on the
edges and vertices of~$\Gamma$.
\item \emph{Complementarity.}
$\mathrm{obs}_g^{\Eone}(\cA) +
\mathrm{obs}_g^{\Eone}(\cA^!) = 0$
in $H^*(\mathcal{M}_{g,1}^{\partial})$,
since the $\Eone$ Koszul duality inverts
the $R$-matrix ($R \to R^{-1}$), which
reverses the orientation of the ribbon
graphs.
\end{enumerate}
For the Yangian $Y(\mathfrak{sl}_2)^{\mathrm{ch}}$,
the ribbon graph expansion at genus~$1$ should recover
$\mathrm{obs}_1 \propto \hbar$ (the deformation parameter),
vanishing at $\hbar = 0$ (the classical limit,
Corollary~\textup{\ref{cor:yangian-classical-self-dual}}).
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\end{conjecture}

\begin{remark}[Scope]\label{rem:e1-genus-scope}
This conjecture requires several foundational
developments: (a)~a theory of compactified configuration
spaces on bordered surfaces with the correct boundary
behavior (extending Fulton--MacPherson to the case
with boundary); (b)~an $\Eone$ analog of the Feynman
transform for the modular operad; (c)~an $\Eone$ analog
of the Faber--Pandharipande formula for tautological
integrals on $\mathcal{M}_{g,1}^{\partial}$.  The
closest existing work is the Swiss-cheese operad
(Voronov~\cite{Voronov99}), which governs open-closed
homotopy algebras.
The toroidal algebra
(Remark~\ref{rem:toroidal-three-theorems}) faces the
same obstruction.

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~I (existence).
The conjecture posits the existence of an $\Eone$ genus theory on bordered Riemann surfaces, extending the chiral bar complex from closed to open surfaces.
\end{remark}


\section{Shifted Yangians}
\label{sec:shifted-yangians}

\subsection{Definition}

\begin{definition}[Shifted Yangian]\label{def:shifted-yangian}
For a coweight $\mu \in X_*(\mathfrak{h})$, the \emph{shifted Yangian} $Y_\mu(\mathfrak{g})$
(Brundan--Kleshchev, Finkelberg--Tsymbaliuk, KWWY) is generated by elements
$E_i^{(r)}, F_i^{(r)}, H_i^{(r)}$ for $i = 1, \ldots, \mathrm{rank}(\mathfrak{g})$
and $r \geq 0$, satisfying the same Yangian relations as $Y(\mathfrak{g})$ except that the
generating function $H_i(u) = \sum_{r \geq 0} H_i^{(r)} u^{-r}$ is constrained to be a rational
function whose numerator and denominator degrees are prescribed by $\mu$:
\[
H_i(u) = \frac{\prod_{j=1}^{\mu_i^+}(u - a_j^{(i)})}{\prod_{j=1}^{\mu_i^-}(u - b_j^{(i)})}
\]
where $\mu_i^\pm = \langle \alpha_i, \mu^\pm \rangle$ and $\mu = \mu^+ - \mu^-$ decomposes the coweight into dominant parts. The parameters $a_j^{(i)}, b_j^{(i)}$ are complex numbers.
\end{definition}

\begin{conjecture}[Shifted Yangian as \texorpdfstring{$\Eone$}{E1}-chiral; \ClaimStatusConjectured]\label{conj:shifted-yangian-e1}
The shifted Yangian admits a chiral algebra structure $Y_\mu(\mathfrak{g})^{\mathrm{ch}}$
that is $\Eone$-chiral.  The shift $\mu$ modifies the central terms in the OPE,
and the rational constraint on $H_i(u)$ introduces additional poles in the vertex
operators.
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\end{conjecture}

\begin{remark}[Scope]
A proof would require: (1)~an explicit vertex operator construction for
the shifted Yangian generators $E_i^{(r)}, F_i^{(r)}, H_i^{(r)}$ with
the rational constraint on $H_i(u)$; (2)~verification of the Borcherds
identity (weak associativity of the OPE) in the presence of the additional
poles introduced by the shift.  For the unshifted case ($\mu = 0$), the
$\Eone$-chiral structure is established in Theorem~\ref{thm:yangian-e1}.
A conjectural extension is that the shifted case follows by an analogous argument using the
BFN construction (Theorem~\ref{thm:bfn}), which realizes the shifted
Yangian as equivariant homology and thus provides a natural source of
vertex operators.  Dimofte--Niu--Py \cite{DNP25} construct dg-shifted Yangians
from line operators in 3d holomorphic QFT, providing further evidence for the
$\Eone$-chiral structure in the shifted setting.

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~I (existence).
The conjecture asserts the existence of an $\Eone$-chiral algebra structure on the shifted Yangian $Y_\mu(\mathfrak{g})$, extending the unshifted construction to non-zero coweights.
\end{remark}

\subsection{Comparison with dg-shifted Yangians}
\label{sec:dg-shifted-comparison}

\begin{proposition}[Structural comparison; \ClaimStatusProvedHere]
\label{prop:dg-shifted-comparison}
\index{Yangian!dg-shifted}
The $\Eone$-chiral Yangian
$Y(\mathfrak{g})^{\mathrm{ch}}$
\textup{(}Theorem~\textup{\ref{thm:yangian-e1})}
and the dg-shifted Yangian
$Y^{\mathrm{dg}}(\mathfrak{g})$
of Dimofte--Niu--Py~\textup{\cite{DNP25}}
share the following structural features:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Both are $\Eone$-deformations of the affine algebra
  $\widehat{\mathfrak{g}}_k$, controlled by the rational
  $R$-matrix $R(u) = 1 + r/u + O(u^{-2})$.
\item Both have generators in RTT form
  $T(u) = 1 + \sum_{r \geq 1} T^{(r)} u^{-r}$
  with quadratic relations
  $R_{12}(u{-}v)\,T_1(u)\,T_2(v) = T_2(v)\,T_1(u)\,R_{12}(u{-}v)$.
\item The Koszul dual of both is the $R^{-1}$-Yangian:
  replacing $R$ by $R^{-1}$ corresponds to
  $\hbar \mapsto -\hbar$.
\item Evaluation modules $V(a)$ and their tensor products
  behave identically in both constructions
  (Proposition~\ref{prop:eval-module-bar}).
\end{enumerate}
The constructions differ in their geometric origins:
$Y(\mathfrak{g})^{\mathrm{ch}}$ arises from FM configuration
space integrals on algebraic curves, while
$Y^{\mathrm{dg}}(\mathfrak{g})$ arises from line operators
in 3d holomorphic Chern--Simons theory~\textup{\cite{DNP25}}.
\end{proposition}

\begin{proof}
Part~(i) follows from comparing the deformation parameter:
both constructions deform the vertex algebra OPE by a
spectral parameter $u = z_1 - z_2$ that controls
$\Eone$-locality.  In the FM picture, $u$ is the
relative coordinate on $\overline{C}_2(X)$
(Theorem~\ref{thm:yangian-e1}).  In the DNP construction,
$u$ is the holomorphic coordinate along the topological
line (the ``spectral parameter'' of \cite[\S5]{DNP25}).

Part~(ii): the RTT presentation is a presentation of the
quadratic algebra, hence determined by the $R$-matrix.
Since both constructions use the same $R$-matrix, the
RTT relations agree.

Part~(iii) follows from Theorem~\ref{thm:yangian-koszul-dual}
(this manuscript) and \cite[Thm.~6.12]{DNP25}
(the Koszul dual of line operators is controlled by $R^{-1}$).

Part~(iv): the bar complex of the evaluation module
is the CE complex $C^*(\mathfrak{g}, V)$
(Proposition~\ref{prop:eval-module-bar}), which
depends only on the underlying $\mathfrak{g}$-action,
not on the geometric origin of the Yangian structure.
\end{proof}

\begin{remark}[Quasi-isomorphism question]
\label{rem:dg-shifted-qi}
The structural comparison above does not establish a
quasi-isomorphism $Y(\mathfrak{g})^{\mathrm{ch}}
\simeq Y^{\mathrm{dg}}(\mathfrak{g})$: this would require
constructing a separated complete RTT-level filtration on the
dg-shifted target whose finite quotients recover the theorematic finite
RTT stages.  Corollary~\ref{cor:yangian-hlevel-comparison-criterion}
shows that once such compatible finite quotients are in place, the
comparison with the coefficientwise RTT completion is formal.
Koszulness (Remark~\ref{rem:yangian-collapse-conj}) remains one natural
route to producing those compatible quotient identifications.
\end{remark}

\begin{remark}[Maurer--Cartan element as twisting morphism]
\label{rem:dnp-mc-twisting}
\index{Maurer--Cartan element!twisting morphism}
\index{Yang--Baxter equation!A-infinity@$A_\infty$}
The dg-shifted Yangian of \cite{DNP25} carries a
Maurer--Cartan element $r(z) \in \cA^! \otimes \cA^!$
satisfying an $A_\infty$ Yang--Baxter equation.
In the bar-cobar framework, this element admits a precise
identification: $r(z)$ is the \emph{twisting morphism}
$\tau\colon \bar{B}(\cA) \to \cA^!$
of Theorem~\ref{thm:bar-cobar-isomorphism-main},
restricted to the degree-$2$ component and evaluated at
spectral parameter~$z$.

Explicitly:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The MC equation $dr + r \star r = 0$ is the
  bar-cobar adjunction equation
  $\partial \tau + \tau \cup \tau = 0$,
  which is equivalent to $d_{\bar{B}}^2 = 0$
  (Theorem~\ref{thm:bar-nilpotency-complete}).
\item The $A_\infty$ Yang--Baxter equation of
  \cite[\S5]{DNP25} is the $\Eone$-chiral generalization:
  the bar complex differential encodes the RTT relation
  (Theorem~\ref{thm:yangian-bar-rtt}), and $d^2 = 0$
  is precisely the Yang--Baxter equation for $R(u)$.
\item The non-renormalization theorem of \cite[Thm.~4.1]{DNP25}
  (OPE of line operators is $1$-loop exact) corresponds to
  the Koszul property: the bar spectral sequence collapses
  at $E_2$, so the $A_\infty$ structure is determined by
  the quadratic ($R$-matrix) data.
\end{enumerate}

The bridge claim (Conjecture~\ref{conj:chiral-dg-shifted-qi}) is:
the $\Eone$-chiral Yangian and the dg-shifted Yangian are two
presentations of one object, one via configuration-space
integrals (this manuscript) and one via holomorphic
Chern--Simons perturbation theory~(\cite{DNP25}).  The missing
input is the Koszulness of the $\Eone$-chiral bar complex
(Remark~\ref{rem:yangian-collapse-conj}).
\end{remark}

\begin{conjecture}[Chiral--dg-shifted quasi-isomorphism; \ClaimStatusConjectured]\label{conj:chiral-dg-shifted-qi}
The $\Eone$-chiral Yangian $Y(\fg)^{\mathrm{ch}}$ of this monograph and the
dg-shifted Yangian $Y^{\mathrm{dg}}(\fg)$ of Dimofte--Niu--Py~\cite{DNP25}
are quasi-isomorphic as $\Eone$-algebras.
\end{conjecture}

\begin{proposition}[Degree-2 mixed-tensor criterion for dg-shifted
local transport; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-degree2-mixed-tensor-criterion}
Let $\Ydg_{\cA}$ be a dg-shifted or factorization-theoretic Yangian
candidate with one-factor fundamental line operator
$L_a^{\mathrm{dg}}(u)\in \End(V)\otimes \End(V(a))$, $V=\mathbb{C}^M$,
and residue operator
$\Xi_a^{\mathrm{dg}}:=\operatorname*{Res}_{u=a}L_a^{\mathrm{dg}}(u)$.
Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the one-factor line operator is functorial for the diagonal
  $\mathfrak{sl}_M$-action and normalized by
  $L_a^{\mathrm{dg}}(u)\to 1$ as $u\to\infty$;
\item the local OPE on the fundamental line is one-loop exact, with
  simple pole computed by the degree-$2$ Maurer--Cartan element
  $r(z)=\tau|_{\deg 2}$ from Remark~\ref{rem:dnp-mc-twisting};
\item $\Xi_a^{\mathrm{dg}}(e_1\otimes e_2)=-\hbar(e_2\otimes e_1)$.
\end{enumerate}
Then $\Xi_a^{\mathrm{dg}}=-\hbar P$ and
$L_a^{\mathrm{dg}}(u)=R_{0a}(u-a)$.
If, moreover, the twisted-coproduct hypotheses of
Corollary~\ref{cor:dg-shifted-rtt-typea-single-line-bootstrap} hold on
universal packets and generic tensor powers, then the dg-shifted local
Yangian packet closes: every universal packet carries the standard
finite-stage evaluation action and $\Delta_{r,0}(N)=0$ for $0\le r\le N$
on the evaluation-generated core.

Equivalently, once the standard RTT side is fixed, the remaining local
transport problem is reduced to transporting the degree-$2$ twisting
coefficient on the ordered mixed-tensor line $e_1\otimes e_2$ to the
standard normalized residue.
\end{proposition}

\begin{proof}
Assumption~\textup{(iii)} is exactly the ordered mixed-tensor formula of
Proposition~\ref{prop:dg-shifted-rtt-typea-uniform-single-line}, while
\textup{(i)} supplies the functoriality and normalization hypotheses
used there and in
Corollary~\ref{cor:dg-shifted-rtt-typea-residue-reduction}, giving
$\Xi_a^{\mathrm{dg}}=-\hbar P$ and $L_a^{\mathrm{dg}}(u)=R_{0a}(u-a)$.
The twisted-coproduct statement follows verbatim from
Corollary~\ref{cor:dg-shifted-rtt-typea-single-line-bootstrap}.
\end{proof}

\begin{corollary}[Seed-normalized extraction of the dg-shifted local
coefficient; \ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-seed-normalized-coefficient}
In the setting of
Proposition~\ref{prop:dg-shifted-rtt-degree2-mixed-tensor-criterion},
write the one-loop singular part in the standard logarithmic
normalization $r_a^{\mathrm{fund}}(z)\,\eta_{12}$,
$\eta_{12}=d\log(z_1-z_2)$,
with $r_a^{\mathrm{fund}}(z)$ the operator-valued degree-$2$ twisting
morphism coefficient induced by $r(z)=\tau|_{\deg 2}$ on
$V\otimes V(a)$.  Then
$\Xi_a^{\mathrm{dg}}=r_a^{\mathrm{fund}}(z)\big|_{z_1=z_2}$,
and the remaining dg-shifted local transport problem is the single
coefficient identity
$r_a^{\mathrm{fund}}(z)(e_1\otimes e_2)=-\hbar(e_2\otimes e_1)$.
\end{corollary}

\begin{proof}
Since $\operatorname*{Res}_{z_1=z_2}\eta_{12}=1$
by \eqref{eq:the-seed}, the residue acts only on the scalar logarithmic
factor and leaves the operator coefficient unchanged.
\end{proof}

\begin{proposition}[Degree-\texorpdfstring{$2$}{2} scalar normalization
and Casimir reduction; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-degree2-scalar-normalization}
Work in the setting of
Corollary~\ref{cor:dg-shifted-rtt-seed-normalized-coefficient} with
$M\ge2$.  Write
$L_a^{\mathrm{dg}}(u)
=1+\hbar\Xi_a^{(1)}/(u-a)+O(\hbar^2)$.
By diagonal $\mathfrak{sl}_M$-functoriality
(Proposition~\ref{prop:dg-shifted-rtt-degree2-mixed-tensor-criterion})
and Schur's lemma on $V\otimes V\cong
\operatorname{Sym}^2(V)\oplus\Lambda^2(V)$,
$\Xi_a^{(1)}=\alpha_a\,\id+\beta_a\,P$.
A scalar renormalization
$L_a^{\mathrm{ren}}(u):=s_a(u)\,L_a^{\mathrm{dg}}(u)$
with $s_a(u)=1+\hbar\gamma_a/(u-a)+O(\hbar^2)$ shifts $\alpha_a$ to
$\alpha_a+\gamma_a$ while leaving $\beta_a$ invariant.  Choosing
$\gamma_a=-\alpha_a$ gives pure-permutation normalization
$L_a^{\mathrm{ren}}(u)=1+\hbar\beta_a P/(u-a)+O(\hbar^2)$, and the
remaining local packet is the single identity $\beta_a=-1$.
\end{proposition}

\begin{proof}
In pure-permutation normalization,
$r_a^{\mathrm{fund}}(z)|_{z_1=z_2}=\hbar\beta_a\,P$ by
Corollary~\ref{cor:dg-shifted-rtt-seed-normalized-coefficient};
on $e_1\otimes e_2$ this equals $-\hbar(e_2\otimes e_1)$ iff
$\beta_a=-1$.
\end{proof}

\begin{corollary}[Trace-zero Casimir convention reduces to the same
scalar packet; \ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-degree2-casimir-normalization}
If $\Xi_a^{(1)}=\lambda_a(P-\frac{1}{M}\id)$, then
$\beta_a=\lambda_a$ and the pure-permutation normalization gives
$\Xi_{a,\mathrm{ren}}^{(1)}=\lambda_a P$.
The remaining input is $\lambda_a=-1$ (choosing
$\gamma_a=\lambda_a/M$ in
Proposition~\ref{prop:dg-shifted-rtt-degree2-scalar-normalization}
cancels the identity channel).
\end{corollary}

\begin{proposition}[Fundamental Casimir insertion fixes the normalized
one-loop scalar; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-degree2-fundamental-casimir}
If $r_a^{\mathrm{fund}}(z)|_{z_1=z_2}
=-\hbar\,\Omega_{\mathfrak{sl}_M}^{\mathrm{fund}}$,
$\Omega_{\mathfrak{sl}_M}^{\mathrm{fund}}:=P-\frac{1}{M}\id$,
then $\lambda_a=\beta_a=-1$, $\Xi_{a,\mathrm{ren}}^{(1)}=-P$, and
$r_{a,\mathrm{ren}}^{\mathrm{fund}}(z)(e_1\otimes e_2)
=-\hbar(e_2\otimes e_1)$.
\end{proposition}

\begin{proof}
On the defining representation,
$\Omega_{\mathfrak{gl}_M}^{\mathrm{fund}}
=\sum_{i,j}E_{ij}\otimes E_{ji}=P$,
so $\Omega_{\mathfrak{sl}_M}^{\mathrm{fund}}=P-\frac{1}{M}\id$, which
is Corollary~\ref{cor:dg-shifted-rtt-degree2-casimir-normalization} with
$\lambda_a=-1$.
\end{proof}

\begin{corollary}[Factorization-side fundamental Casimir identity;
\ClaimStatusProvedHere]
\label{cor:factorization-fundamental-casimir-identity}
On the ordered fundamental evaluation line of
$\operatorname{Fact}_{\Eone}^{\mathrm{eval}}(Y_\hbar(\mathfrak{sl}_M))$,
$r_{a,\mathrm{fact}}^{\mathrm{fund}}(z)|_{z_1=z_2}
=-\hbar(P-\frac{1}{M}\id)$,
$r_{a,\mathrm{fact,ren}}^{\mathrm{fund}}(z)|_{z_1=z_2}=-\hbar P$, and
$\beta_a=-1$.
The factorization side of the local type-$A$ packet is already closed.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:dg-shifted-rtt-standard-typea-local-packet} gives
$L_a^{\mathrm{std}}(u)=1-\hbar P/(u-a)$
(Theorem~\ref{thm:yangian-e1}); the Casimir conversion follows from
Corollary~\ref{cor:dg-shifted-rtt-degree2-casimir-normalization} and
Proposition~\ref{prop:dg-shifted-rtt-degree2-fundamental-casimir}.
\end{proof}

\begin{proposition}[Shared bar seed transports the fundamental
degree-\texorpdfstring{$2$}{2} coefficient; \ClaimStatusProvedHere]
\label{prop:dg-shifted-factorization-shared-seed}
If the dg-shifted and factorization fundamental-line degree-$2$
coefficients are both induced by $r(z)=\tau|_{\deg 2}$
(Remark~\ref{rem:dnp-mc-twisting}) on $V\otimes V(a)$, then
$r_{a,\mathrm{dg}}^{\mathrm{fund}}(z)|_{z_1=z_2}
=r_{a,\mathrm{fact}}^{\mathrm{fund}}(z)|_{z_1=z_2}
=-\hbar(P-\frac{1}{M}\id)$
and $r_{a,\mathrm{dg,ren}}^{\mathrm{fund}}(z)(e_1\otimes e_2)
=-\hbar(e_2\otimes e_1)$.
\end{proposition}

\begin{proof}
The shared seed forces equality of the two coefficients;
Corollary~\ref{cor:factorization-fundamental-casimir-identity}
identifies the factorization side with the Casimir insertion;
Proposition~\ref{prop:dg-shifted-rtt-degree2-fundamental-casimir}
gives $\beta_a=-1$.
\end{proof}

\begin{corollary}[Shared bar seed closes the local dg-shifted
type-\texorpdfstring{$A$}{A} MC4 packet; \ClaimStatusProvedHere]
\label{cor:yangian-typea-dg-local-closure}
Under the hypotheses of
Corollary~\ref{cor:yangian-typea-degree2-plus-generators} with the
shared bar seed of
Proposition~\ref{prop:dg-shifted-factorization-shared-seed},
item~\textup{(a)} is automatic and the remaining MC4 input is the DK-5
categorical packet
(Proposition~\ref{prop:yangian-dk5-fundamental-packet}).
\end{corollary}

\begin{proof}
Proposition~\ref{prop:dg-shifted-factorization-shared-seed} gives
item~\textup{(a)} of
Corollary~\ref{cor:yangian-typea-degree2-plus-generators}.
\end{proof}

\begin{conjecture}[Finite-RTT quotient package on a dg model of the
canonical Yangian H-level target;
\ClaimStatusConjectured]
\label{conj:dg-shifted-yangian-rtt-package}
Let $\cA=\mathcal{Y}(\mathfrak{sl}_M)$,
$\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA}$
(Proposition~\ref{prop:yangian-canonical-hlevel-target}), and
$U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$
(Proposition~\ref{prop:yangian-canonical-envelope}).  There exists a
separated complete dg algebra $\Ydg_{\cA}$ (pole-order filtration),
quasi-isomorphic to $U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ and
admitting an RTT-adapted filtration
(Definition~\ref{def:rtt-adapted-filtration}): the filtration is
separated and complete for RTT level;
$\Ydg_{\cA}/F^{N+1}\Ydg_{\cA}$ records exactly the modes up to level
$N$; those quotients are dg quasi-isomorphic to $Y_{\le N}$; and the
comparison is compatible with evaluation modules and
$r(z)=\tau|_{\deg 2}$.  Assuming this,
Corollary~\ref{cor:yangian-hlevel-comparison-criterion} identifies
$\Ydg_{\cA}$ with $\widehat Y_{\mathrm{RTT}}$.
\end{conjecture}

\begin{remark}[Why line operators should control the filtration]
\label{rem:dg-shifted-filtration-evidence}
The canonical H-level target already exists (Proposition~\ref{prop:yangian-canonical-hlevel-target}); the remaining MC4 problem is to equip it with compatible RTT-level quotients.  Line-operator OPEs are organized by pole order, matching the RTT filtration, and the Maurer--Cartan element $r(z)$ appears as the degree-$2$ bar twisting morphism.
\end{remark}

\begin{remark}[First attack route for dg-shifted RTT quotients]
\label{rem:dg-shifted-quotient-route}
Conjecture~\ref{conj:dg-shifted-yangian-rtt-package} reduces to four stagewise checks: (i)~RTT-level ideals are preserved by the differential and coproduct; (ii)~the level-$N$ quotient depends only on the first $N$ OPE modes; (iii)~that quotient is identified with $Y_{\le N}$ via $R$-matrix relations; (iv)~the induced degree-$2$ twisting morphism matches $\tau|_{\deg 2}$.

The reduction chain then contracts: locality criterion (Proposition~\ref{prop:dg-shifted-rtt-locality-criterion}) $\to$ kernel coefficient criterion (Proposition~\ref{prop:dg-shifted-rtt-kernel-coefficient-criterion}) $\to$ evaluation detection (Proposition~\ref{prop:dg-shifted-rtt-evaluation-detection}) $\to$ boundary seed (Proposition~\ref{prop:dg-shifted-rtt-boundary-seed}) $\to$ fundamental propagation (Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation}) $\to$ auxiliary kernel identification.  For type~$A$, the entire chain collapses to a single ordered mixed-tensor check $\Xi_a(e_1\otimes e_2)=-\hbar(e_2\otimes e_1)$ (Corollary~\ref{cor:dg-shifted-rtt-typea-single-line}), which after scalar normalization reduces to the Casimir identity (Proposition~\ref{prop:dg-shifted-rtt-degree2-fundamental-casimir}).  This identity already holds on the factorization target (Corollary~\ref{cor:factorization-fundamental-casimir-identity}), so the remaining frontier is the H-level realization of the dg-shifted target with compact generators.
\end{remark}

The following chain of propositions establishes successively weaker
sufficient conditions for identifying $Q_N:=\Ydg_{\cA}/F^{N+1}\Ydg_{\cA}$
with $Y_{\le N}$; each implies the preceding one.

\begin{proposition}[Presentation-level criterion for finite RTT
dg quotients; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-presentation-criterion}
Let $\Ydg_{\cA}$ have preserved RTT-level ideals $F^{N+1}\Ydg_{\cA}$
(Proposition~\ref{prop:dg-shifted-quotient-criterion}).  If
$Q_N:=\Ydg_{\cA}/F^{N+1}\Ydg_{\cA}$ is generated by the $T_{ij}^{(r)}$
with $r \le N$, these satisfy the truncated RTT relations and no
further, and evaluation modules agree with the finite RTT stage, then
$Q_N\cong Y_{\le N}$.  With compatible dg structure and $\tau|_{\deg 2}$,
$Q_N$ supplies the $N$th stage of
Conjecture~\ref{conj:dg-shifted-yangian-rtt-package}.
\end{proposition}

\begin{proof}
Universal property of the truncated RTT presentation gives the
isomorphism; evaluation compatibility pins down the identification.
\end{proof}

\begin{proposition}[Pole-order locality criterion for finite RTT
quotients; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-locality-criterion}
Assume $\Ydg_{\cA}$ is topologically generated by RTT modes
$T_{ij}^{(r)}$, and let $F^{N+1}\Ydg_{\cA}$ be the closed two-sided
ideal generated by modes with $r > N$.  If the structure formulas are
RTT-triangular --- every term in $d(T_{ij}^{(r)})$,
$\partial(T_{ij}^{(r)})$, the MC twisting, and
$\Delta^{\mathrm{tw}}(T_{ij}^{(r)})$ contains a factor $T_{ab}^{(s)}$
with $s \ge r$, and the level-$\ell$ part depends only on modes with
$s \le \ell$ --- then $F^{N+1}\Ydg_{\cA}$ is preserved by all four
operations and $Q_N$ depends only on the first $N$ modes.
With truncated RTT relations, evaluation compatibility, and degree-$2$
twisting,
Propositions~\ref{prop:dg-shifted-quotient-criterion}
and~\ref{prop:dg-shifted-rtt-presentation-criterion} identify $Q_N$
with $Y_{\le N}$.
\end{proposition}

\begin{proof}
RTT-triangularity ensures the ideal is preserved (levels $>N$ stay in
the ideal) and the quotient depends only on levels $\le N$.
\end{proof}

\begin{proposition}[RTT-level preservation from the rational
line-operator formulas; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-formula-preservation}
Write $T(z,u)=1+\hbar\sum_{r \ge 0} T^{(r)}(z)\,u^{-r-1}$ and let
$F^{N+1}\Ydg_{\cA}$ be the closed ideal generated by $T^{(r)}(z)$ with
$r>N$.  If the differential and translation act coefficientwise, the
Maurer--Cartan correction comes from the rational convolution
$r(u-v)=\sum r_m(u-v)^{-m-1}$ (so level-$\ell$ terms depend only on
$T^{(a)}$ with $a\le\ell$), and the twisted coproduct satisfies
$\Delta^{\mathrm{tw}}T^{(\ell)}=\sum_{a+b=\ell}T^{(a)}\otimes T^{(b)}$,
then $F^{N+1}\Ydg_{\cA}$ satisfies the hypotheses of
Proposition~\ref{prop:dg-shifted-rtt-locality-criterion}: the ideals
are preserved and $Q_N$ depends only on $T^{(r)}$ with $r \le N$.
\end{proposition}

\begin{proof}
The differential and translation preserve RTT level; the rational
kernel's nonnegative pole order ensures level-$\ell$ depends only on
levels $\le\ell$; the coproduct formula
$\sum_{a+b=\ell}T^{(a)}\otimes T^{(b)}$ has the same property.
\end{proof}

\begin{proposition}[Coefficient-level RTT criterion for finite-stage
identification; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-coefficient-criterion}
Fix $N \ge 0$ and let $Q_N$ be as in
Proposition~\ref{prop:dg-shifted-rtt-formula-preservation}.  If the
truncated monodromy matrix $T_N(u)=1+\hbar\sum_{0\le r\le N}T^{(r)}u^{-r-1}$
satisfies the standard truncated RTT relation in~$Q_N$, the
$T^{(r)}_{ij}$ with $r\le N$ generate $Q_N$ with no further relations,
and the evaluation modules coincide with the standard ones, then
$Q_N\cong Y_{\le N}$.  If also $\tau|_{\deg 2}$ matches, then $Q_N$
realizes the $N$th stage of
Conjecture~\ref{conj:dg-shifted-yangian-rtt-package}.
\end{proposition}

\begin{proof}
The truncated RTT presentation identifies the algebra with $Y_{\le N}$
(Proposition~\ref{prop:dg-shifted-rtt-presentation-criterion});
evaluation compatibility pins down the identification.
\end{proof}

\begin{proposition}[Kernel-coefficient criterion for finite RTT
identification; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-kernel-coefficient-criterion}
Fix $N \ge 0$ and let $Q_N$ be as in
Proposition~\ref{prop:dg-shifted-rtt-formula-preservation}.  Write the
OPE as $\sum K_{a,b}\,u^{-a-1}v^{-b-1}$.  If each $K_{a,b}$ agrees
with the standard finite RTT coefficient, these generate all relations,
and evaluation modules match, then
Proposition~\ref{prop:dg-shifted-rtt-coefficient-criterion} applies and
$Q_N\cong Y_{\le N}$.
\end{proposition}

\begin{proof}
The kernel coefficients are the truncated RTT relations.
\end{proof}

\begin{proposition}[One-loop kernel identity criterion for finite RTT
quotients; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-oneloop-kernel-criterion}
Fix $N \ge 0$ and let $Q_N$ be as in
Proposition~\ref{prop:dg-shifted-rtt-kernel-coefficient-criterion}.
Define the extracted coefficient
$\mathsf{K}^{\mathrm{line}}_{a,b}(N):=
\operatorname{Coeff}_{u^{-a-1}v^{-b-1}}
(R(u-v)\,T_{N,1}(u)\,T_{N,2}(v)
-T_{N,2}(v)\,T_{N,1}(u)\,R(u-v))$
in $\End(V)^{\otimes 2}\otimes Q_N$, and let
$\mathsf{K}^{\mathrm{RTT}}_{a,b}(N)$ denote the standard truncated RTT
coefficient.  If the OPE is one-loop exact,
$\mathsf{K}^{\mathrm{line}}_{a,b}(N)
=\mathsf{K}^{\mathrm{RTT}}_{a,b}(N)$ for all $a,b \le N$, and the
evaluation modules match, then
Proposition~\ref{prop:dg-shifted-rtt-kernel-coefficient-criterion}
applies and $Q_N\cong Y_{\le N}$.
\end{proposition}

\begin{proof}
One-loop exactness and mode-by-mode identity give the
kernel-coefficient hypotheses; evaluation compatibility carries through.
\end{proof}

\begin{proposition}[Evaluation-detection criterion for one-loop RTT
identities; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-evaluation-detection}
Fix $N \ge 0$ and let
$\Delta_{a,b}(N):=
\mathsf{K}^{\mathrm{line}}_{a,b}(N)
-\mathsf{K}^{\mathrm{RTT}}_{a,b}(N)
\in \End(V)^{\otimes 2}\otimes Q_N$
be the coefficient defect.  If $Q_N$ is represented faithfully on tensor
products of fundamental evaluation modules and $\Delta_{a,b}(N)$ acts by
zero on that subcategory for all $a,b \le N$ with standard evaluation
action, then $\Delta_{a,b}(N)=0$ in $Q_N$ and
Proposition~\ref{prop:dg-shifted-rtt-oneloop-kernel-criterion} applies.
\end{proposition}

\begin{proof}
Faithfulness forces $\Delta_{a,b}(N)=0$; evaluation compatibility
carries through.
\end{proof}

\begin{proposition}[Boundary-seed criterion for truncated RTT
defects; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-boundary-seed}
Fix $N \ge 0$ and let $\Delta_{a,b}(N)$ be the coefficient defect of
Proposition~\ref{prop:dg-shifted-rtt-evaluation-detection}.  If the
spectral recursion $\Delta_{a+1,b}(N)=\Delta_{a,b+1}(N)$ holds for
$a+b+1\le N$, the boundary defects $\Delta_{a,0}(N)$ act by zero on the
faithful evaluation family for $0\le a\le N$, and the evaluation action
is standard, then $\Delta_{a,b}(N)=0$ for $a+b\le N$, so
Proposition~\ref{prop:dg-shifted-rtt-evaluation-detection} is satisfied
after checking only $\{\Delta_{a,0}(N)\}_{0 \le a \le N}$.
\end{proposition}

\begin{proof}
The recursion gives $\Delta_{a,b}(N)=\Delta_{a+b,0}(N)$; faithfulness
and boundary vanishing force all defects to vanish.
\end{proof}

\begin{proposition}[Boundary-strip coefficient formula on the
evaluation packet; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-boundary-coefficient-formula}
Let $T_1(u)=\sum_{r\ge 0} T_1^{(r)}u^{-r}$,
$T_2(v)=\sum_{s\ge 0} T_2^{(s)}v^{-s}$ be the normalized fundamental
monodromy series, and expand
$R(u-v)=1-\hbar\sum_{t\ge 0} P_{12}\,u^{-t-1}v^t$ for $|u|>|v|$.
Then
\begin{multline*}
\operatorname{Coeff}_{u^{-a-1}v^{-1}}
\bigl(
R(u\!-\!v)\,T_1(u)\,T_2(v)-T_2(v)\,T_1(u)\,R(u\!-\!v)
\bigr)\\
=\;
T_1^{(a+1)}T_2^{(1)}-T_2^{(1)}T_1^{(a+1)}
-\hbar\!\sum_{t=0}^{a}\!
\bigl(
P_{12}\,T_1^{(a-t)}T_2^{(t+1)}
-T_2^{(t+1)}T_1^{(a-t)}P_{12}
\bigr).
\end{multline*}
\end{proposition}

\begin{proof}
Write $R^{(t)}=-\hbar P_{12}$.  The identity part of $R$ gives the
commutator term; matching $u$- and $v$-powers in the $R$-series forces
$T_1^{(a-t)}$ and $T_2^{(t+1)}$, and summing over $0\le t\le a$ yields
the result.
\end{proof}

\begin{proposition}[Explicit coefficient formula for the fundamental
monodromy series; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-fundamental-coefficient-formula}
Fix generic evaluation points $a_1,\dots,a_m$ and write
\[
T^{(m)}(u)=L_{a_1}(u)\cdots L_{a_m}(u)
=\sum_{r\ge0}T^{(m,r)}u^{-r},
\qquad
L_{a_j}(u)=1-\frac{\hbar P_{0j}}{u-a_j},
\]
on the tensor product
\[
M_m:=V_{\mathrm{fund}}(a_1)\otimes\cdots\otimes
V_{\mathrm{fund}}(a_m).
\]
Then
\[
T^{(m,0)}=1,
\]
and for every $r\ge1$ one has
\[
T^{(m,r)}
=
\sum_{s=1}^{\min(r,m)}(-\hbar)^s
\sum_{1\le j_1<\cdots<j_s\le m}
\sum_{\substack{n_1,\dots,n_s\ge0\\ n_1+\cdots+n_s=r-s}}
a_{j_1}^{n_1}\cdots a_{j_s}^{n_s}\,
P_{0j_1}\cdots P_{0j_s}.
\]
In particular, every summand of $T^{(m,r)}$ is supported on at most
$r$ quantum slots.
\end{proposition}

\begin{proof}
For each factor one has the geometric-series expansion
\[
L_{a_j}(u)
=
1-\hbar\sum_{n\ge0}a_j^n u^{-n-1}P_{0j}
\]
in the standard region $|u|>|a_j|$.  Multiplying the $m$ factors in the
fixed order $j=1,\dots,m$, the coefficient of $u^{-r}$ is obtained by
choosing the non-identity term from exactly $s$ factors
$j_1<\cdots<j_s$ and the identity term from the rest.  If the chosen
terms have degrees $n_1+1,\dots,n_s+1$, then the total $u$-degree
condition is
\[
(n_1+1)+\cdots+(n_s+1)=r,
\]
equivalently $n_1+\cdots+n_s=r-s$.  The contribution of that choice is
\[
(-\hbar)^s a_{j_1}^{n_1}\cdots a_{j_s}^{n_s}
P_{0j_1}\cdots P_{0j_s},
\]
and summing over all subsets and all nonnegative tuples
$(n_1,\dots,n_s)$ gives the displayed formula.

The final sentence is immediate: a summand with $s$ chosen factors
acts nontrivially only on the corresponding $s$ quantum slots, and
$s\le r$.
\end{proof}

\begin{corollary}[Line-side boundary-strip support bound on generic
tensor powers; \ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-boundary-support-bound}
In the setting of
Proposition~\ref{prop:dg-shifted-rtt-fundamental-coefficient-formula},
let
\[
\mathsf{K}^{\mathrm{line},(m)}_{a,0}
:=
\operatorname{Coeff}_{u^{-a-1}v^{-1}}
\Bigl(
R(u-v)\,T_1(u)\,T_2(v)-T_2(v)\,T_1(u)\,R(u-v)
\Bigr)
\]
be the line-side boundary-strip coefficient on $M_m$, with
$T_i$ written on the $i$th auxiliary copy of~$V$.  Then every summand
of $\mathsf{K}^{\mathrm{line},(m)}_{a,0}$ is supported on at most
$a+1$ quantum slots.

Equivalently, on the standard type-$A$ fundamental evaluation packet
the line-side half of the finite-detection reduction is already
compatible with the slot bound appearing in
Proposition~\ref{prop:dg-shifted-rtt-finite-tensor-detection}.
\end{corollary}

\begin{proof}
By
Proposition~\ref{prop:dg-shifted-rtt-boundary-coefficient-formula},
\[
\mathsf{K}^{\mathrm{line},(m)}_{a,0}
=
T_1^{(a+1)}T_2^{(1)}-T_2^{(1)}T_1^{(a+1)}
-\hbar\sum_{t=0}^{a}
\Bigl(
P_{12}\,T_1^{(a-t)}T_2^{(t+1)}
-T_2^{(t+1)}T_1^{(a-t)}P_{12}
\Bigr).
\]
By
Proposition~\ref{prop:dg-shifted-rtt-fundamental-coefficient-formula},
every summand of $T_1^{(a+1)}$ is supported on a subset
$S\subset\{1,\dots,m\}$ with $|S|\le a+1$, while every summand of
$T_2^{(1)}$ is supported on a single slot $\{k\}$.  If $k\notin S$,
the two summands commute because they act on distinct quantum slots,
so their contribution cancels in the commutator
$T_1^{(a+1)}T_2^{(1)}-T_2^{(1)}T_1^{(a+1)}$.  Thus every surviving
summand of the commutator is supported on at most $|S|\le a+1$ quantum
slots.

For the $t$th summand of the remaining series, every summand of
$T_1^{(a-t)}$ is supported on at most $a-t$ quantum slots and every
summand of $T_2^{(t+1)}$ is supported on at most $t+1$ quantum slots.
Since $P_{12}$ acts only on auxiliary spaces, it does not enlarge the
quantum support.  Therefore every summand of
$P_{12}\,T_1^{(a-t)}T_2^{(t+1)}$ and of
$T_2^{(t+1)}T_1^{(a-t)}P_{12}$ is supported on at most
$(a-t)+(t+1)=a+1$ quantum slots.

Combining the two cases proves the claim.
\end{proof}

\begin{proposition}[Defect-side support mechanism from RTT degree;
\ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-defect-support-mechanism}
Fix $N \ge 0$, $0\le a\le N$, and a generic tensor product
\[
M_m:=V_{\mathrm{fund}}(a_1)\otimes\cdots\otimes
V_{\mathrm{fund}}(a_m).
\]
Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the action of the truncated monodromy coefficients on $M_m$ is
  induced by the coefficientwise twisted-coproduct multiplication law
  of Proposition~\ref{prop:dg-shifted-rtt-formula-preservation}; and
\item the boundary-strip defect $\Delta_{a,0}(N)$ is homogeneous of RTT
  degree $a+1$.
\end{enumerate}
Then every summand in the action of $\Delta_{a,0}(N)$ on $M_m$ is
supported on at most $a+1$ quantum slots.  Consequently the action of
$\Delta_{a,0}(N)$ on a tensor product of arbitrary length is
determined by its restrictions to the generic tensor subproducts of
length at most $a+1$.

In the standard type-$A$ fundamental packet, this is the defect-side
counterpart of
Corollary~\ref{cor:dg-shifted-rtt-boundary-support-bound}.
\end{proposition}

\begin{proof}
By
Proposition~\ref{prop:dg-shifted-rtt-formula-preservation},
the iterated twisted coproduct on a tensor power is obtained by
coefficientwise multiplication of monodromy matrices.  Therefore every
tensor summand occurring in the action of a homogeneous degree-$(a+1)$
monomial in the coefficients $T^{(r)}$ is indexed by a decomposition
\[
d_1+\cdots+d_s=a+1,
\qquad d_i\ge1,
\]
over the active tensor factors.  Since each active factor contributes
positive RTT degree, one necessarily has $s\le a+1$.  Thus every such
tensor summand is supported on at most $a+1$ quantum slots.

The defect $\Delta_{a,0}(N)$ is a finite linear combination of such
homogeneous monomials by assumption~\textup{(ii)}, so the same support
bound holds for every summand in its action on $M_m$.  The final
sentence is immediate: on a longer tensor product, each summand factors
through one of the generic subproducts supported on at most $a+1$
slots.
\end{proof}

\begin{proposition}[Universal generic packet reduction for the
boundary strip; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-universal-generic-packets}
Fix $m\ge1$ and algebraically independent parameters
$x_1,\dots,x_m$.  Write
\[
K_m:=\mathbb{C}(x_1,\dots,x_m),
\qquad
M_m^{\mathrm{gen}}
:=
V_{\mathrm{fund}}(x_1)\otimes_{K_m}\cdots\otimes_{K_m}
V_{\mathrm{fund}}(x_m).
\]
Assume the line-side monodromy on $M_m^{\mathrm{gen}}$ is given by the
fundamental product
\[
L_{x_1}(u)\cdots L_{x_m}(u),
\qquad
L_{x_j}(u)=1-\frac{\hbar P_{0j}}{u-x_j},
\]
and that the truncated quotient acts by the standard evaluation
formulas of Proposition~\ref{prop:dg-shifted-rtt-evaluation-detection}.
Then for every $a\le N$, the matrix entries of the operators
\[
\mathsf{K}^{\mathrm{line},(m)}_{a,0},
\qquad
\mathsf{K}^{\mathrm{RTT},(m)}_{a,0},
\qquad
\Delta^{(m)}_{a,0}(N)
:=
\mathsf{K}^{\mathrm{line},(m)}_{a,0}
-\mathsf{K}^{\mathrm{RTT},(m)}_{a,0}
\]
on $M_m^{\mathrm{gen}}$ lie in the polynomial ring
$\mathbb{C}[x_1,\dots,x_m]$.

For any generic specialization
\[
x_i\mapsto \alpha_i
\qquad (\alpha_i\neq \alpha_j \text{ for } i\neq j),
\]
the specialized operator is exactly the action of the same boundary
coefficient on
\[
V_{\mathrm{fund}}(\alpha_1)\otimes\cdots\otimes
V_{\mathrm{fund}}(\alpha_m).
\]
Consequently $\Delta_{a,0}(N)$ vanishes on every generic tensor product
of length $m$ if and only if it vanishes on the single universal
generic packet $M_m^{\mathrm{gen}}$.
\end{proposition}

\begin{proof}
By
Proposition~\ref{prop:dg-shifted-rtt-fundamental-coefficient-formula},
each monodromy coefficient on the line side is a finite sum of terms
\[
(-\hbar)^s x_{j_1}^{n_1}\cdots x_{j_s}^{n_s} P_{0j_1}\cdots P_{0j_s},
\]
so its matrix entries lie in $\mathbb{C}[x_1,\dots,x_m]$.  The
boundary-strip formula of
Proposition~\ref{prop:dg-shifted-rtt-boundary-coefficient-formula}
expresses $\mathsf{K}^{\mathrm{line},(m)}_{a,0}$ as a finite
polynomial combination of those coefficients, hence its matrix entries
also lie in $\mathbb{C}[x_1,\dots,x_m]$.

On the RTT side, the standard evaluation action uses the same
coefficientwise monodromy formulas at finite stage, so the matrix
entries of $\mathsf{K}^{\mathrm{RTT},(m)}_{a,0}$ are polynomial in the
same parameters.  Therefore the same is true for the defect
$\Delta^{(m)}_{a,0}(N)$.

Specializing $x_i\mapsto\alpha_i$ simply evaluates those polynomial
matrix entries at the chosen distinct parameters, which is exactly the
generic tensor product
$V_{\mathrm{fund}}(\alpha_1)\otimes\cdots\otimes
V_{\mathrm{fund}}(\alpha_m)$.  If the operator on
$M_m^{\mathrm{gen}}$ is zero, then all of its polynomial matrix entries
are zero, so every generic specialization is zero as well.  The
converse follows because a polynomial matrix entry that vanishes on
every point of the open set $\{\alpha_i\neq\alpha_j\}$ must vanish
identically.
\end{proof}

\begin{corollary}[Minimal canonical family from the boundary-strip
induction; \ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-minimal-canonical-family}
Fix $0\le a\le N$.  Under the hypotheses of
Proposition~\ref{prop:dg-shifted-rtt-defect-support-mechanism} and
Proposition~\ref{prop:dg-shifted-rtt-universal-generic-packets}, to
prove
\[
\Delta_{a,0}(N)=0
\]
it is enough to verify vanishing on the canonical universal packets
\[
M_m^{\mathrm{gen}}
\qquad (1\le m\le a+1).
\]
Conversely, any all-rank induction proving $\Delta_{a,0}(N)=0$ must in
particular kill these packets.  Hence this family is the minimal
canonical subproduct family furnished by the present boundary-strip
reduction.
\end{corollary}

\begin{proof}
By
Proposition~\ref{prop:dg-shifted-rtt-defect-support-mechanism},
the action of $\Delta_{a,0}(N)$ on an arbitrary generic tensor product
is determined by its restrictions to the subproducts of lengths at most
$a+1$.  By
Proposition~\ref{prop:dg-shifted-rtt-universal-generic-packets}, each
fixed tensor length contributes only one universal generic packet up to
specialization.  Therefore vanishing on the displayed family forces
vanishing on every generic tensor product relevant to the
finite-detection argument.

The converse is tautological: if $\Delta_{a,0}(N)$ vanishes on every
generic tensor product, then it vanishes on these particular universal
ones.  This is the smallest family produced by combining the
length-$(a+1)$ support reduction with the collapse of each fixed tensor
length to one universal generic packet.
\end{proof}

\begin{proposition}[Finite tensor-length detection for boundary-strip RTT
defects; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-finite-tensor-detection}
Fix $N \ge 0$ and let
\[
V_{\mathrm{fund}}(a):=\mathbb{C}^N(a)
\]
denote the fundamental evaluation module of
$Y(\mathfrak{sl}_N)$.  Let
\[
\Delta_{a,0}(N)
=\mathsf{K}^{\mathrm{line}}_{a,0}(N)
-\mathsf{K}^{\mathrm{RTT}}_{a,0}(N)
\]
be the boundary-strip defect family from
Proposition~\ref{prop:dg-shifted-rtt-boundary-seed}.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item for each $0 \le a \le N$, the defect $\Delta_{a,0}(N)$ is
  homogeneous of RTT degree $a+1$;
\item on each generic tensor product
  \[
  V_{\mathrm{fund}}(a_1)\otimes\cdots\otimes
  V_{\mathrm{fund}}(a_m),
  \]
  the action of the truncated monodromy coefficients is induced by the
  coefficientwise twisted-coproduct multiplication law of
  Proposition~\ref{prop:dg-shifted-rtt-formula-preservation};
\item on those same generic tensor products, the truncated quotient
  acts by the standard evaluation formulas of
  Proposition~\ref{prop:dg-shifted-rtt-evaluation-detection};
\item the faithful evaluation subcategory of
  Proposition~\ref{prop:dg-shifted-rtt-evaluation-detection} is
  generated under finite direct sums, tensor products, and subquotients
  by generic tensor products
  \[
  V_{\mathrm{fund}}(a_1)\otimes\cdots\otimes V_{\mathrm{fund}}(a_m)
  \qquad (a_i\neq a_j \text{ for } i\neq j);
  \]
\item vanishing of a coefficient defect on those generic tensor products
  is preserved under finite direct sums, tensor products, and
  subquotients; and
\item for every $0 \le a \le N$, the defect $\Delta_{a,0}(N)$ acts by
  zero on each canonical universal generic packet
  \[
  M_m^{\mathrm{gen}}
  :=
  V_{\mathrm{fund}}(x_1)\otimes_{\mathbb{C}(x_1,\dots,x_m)}\cdots
  \otimes_{\mathbb{C}(x_1,\dots,x_m)}V_{\mathrm{fund}}(x_m)
  \qquad (1\le m\le a+1).
  \]
\end{enumerate}
Then $\Delta_{a,0}(N)=0$ for all $0 \le a \le N$.  Consequently the
boundary-strip reduction of
Proposition~\ref{prop:dg-shifted-rtt-boundary-seed} is discharged after
checking only the canonical universal generic packets of lengths at
most $N+1$, together with the standard evaluation action of $T_N(u)$ on
those packets.
\end{proposition}

\begin{proof}
Fix $a \le N$.  By
Corollary~\ref{cor:dg-shifted-rtt-minimal-canonical-family},
assumptions~\textup{(i)}, \textup{(ii)}, \textup{(iii)},
and~\textup{(vi)} imply that all generic tensor-product actions of
$\Delta_{a,0}(N)$ vanish.
Therefore $\Delta_{a,0}(N)$ acts trivially on every generic tensor
product built from fundamental evaluation modules, regardless of
length.  Assumptions~\textup{(iv)} and~\textup{(v)} then propagate
this vanishing to the whole faithful evaluation subcategory of
Proposition~\ref{prop:dg-shifted-rtt-evaluation-detection}.  That
proposition therefore forces the quotient identity
\[
\Delta_{a,0}(N)=0.
\]

Doing this for all $a\le N$ kills the entire boundary strip, so
Proposition~\ref{prop:dg-shifted-rtt-boundary-seed} reduces the full
RTT defect family to this finite canonical family of universal generic
packets.
\end{proof}

\begin{proposition}[Top-packet induction step on the universal family;
\ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-top-packet-induction}
Set $m:=a+1$ and let
\[
M_m^{\mathrm{gen}}
=
V_{\mathrm{fund}}(x_1)\otimes_{\mathbb{C}(x_1,\dots,x_m)}\cdots
\otimes_{\mathbb{C}(x_1,\dots,x_m)}V_{\mathrm{fund}}(x_m)
\]
be the top universal packet for the boundary index~$a$.  Let
\[
\mathsf{F}_{<m}\End(V^{\otimes 2}\otimes M_m^{\mathrm{gen}})
\]
be the linear span of operators supported on proper subsets of the
quantum slots $\{1,\dots,m\}$.  Assume the hypotheses of
Proposition~\ref{prop:dg-shifted-rtt-defect-support-mechanism} and that
\[
\Delta_{a,0}(N)
\]
acts by zero on the universal packets $M_r^{\mathrm{gen}}$ for every
$1\le r\le a$.  Then
\[
\Delta^{(m)}_{a,0}(N)=0
\quad\Longleftrightarrow\quad
\bigl[\Delta^{(m)}_{a,0}(N)\bigr]=0
\ \text{in}\ 
\End(V^{\otimes 2}\otimes M_m^{\mathrm{gen}})/\mathsf{F}_{<m}.
\]
Equivalently, once the shorter universal packets are killed, the
induction from packet lengths $\le a$ to the top packet $m=a+1$
closes exactly on the top-support class.
\end{proposition}

\begin{proof}
By
Proposition~\ref{prop:dg-shifted-rtt-defect-support-mechanism}, every
summand in the action of $\Delta_{a,0}(N)$ on $M_m^{\mathrm{gen}}$ is
supported on at most $m=a+1$ quantum slots.  Therefore modulo
$\mathsf{F}_{<m}$ only the full-support part can survive.

If a summand is supported on a proper subset
$S\subsetneq\{1,\dots,m\}$, then it factors through the corresponding
universal packet $M_{|S|}^{\mathrm{gen}}$ with $|S|\le a$, so it
vanishes by hypothesis.  Hence
$\Delta^{(m)}_{a,0}(N)$ vanishes if and only if its class in the
quotient by $\mathsf{F}_{<m}$ vanishes.
\end{proof}

\begin{proposition}[Closed-form line-side top-support class on the top
packet; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-top-packet-line-formula}
In the setting of
Proposition~\ref{prop:dg-shifted-rtt-top-packet-induction}, relabel the
two auxiliary copies by $\alpha,\beta$ and the $m=a+1$ quantum slots by
$1,\dots,m$.  For an ordered subset
$S=\{s_1<\cdots<s_r\}\subseteq [m]$, write
\[
P_{\alpha,S}:=P_{\alpha s_1}\cdots P_{\alpha s_r},
\qquad
P_{\beta,S}:=P_{\beta s_1}\cdots P_{\beta s_r},
\]
and let $S^c=[m]\setminus S$.  Then the image of the line-side boundary
coefficient
\[
\mathsf{K}^{\mathrm{line},(m)}_{a,0}
\]
in the quotient
\[
\End(V^{\otimes 2}\otimes M_m^{\mathrm{gen}})/\mathsf{F}_{<m}
\]
is represented by the parameter-free operator
\[
\Omega_a^{\mathrm{line}}
:=
(-\hbar)^{a+2}
\left[
\sum_{j=1}^{m}
\bigl(
P_{\alpha,[m]}P_{\beta,j}-P_{\beta,j}P_{\alpha,[m]}
\bigr)
+\sum_{S\subsetneq [m]}
\bigl(
P_{\alpha\beta}P_{\alpha,S}P_{\beta,S^c}
-P_{\beta,S^c}P_{\alpha,S}P_{\alpha\beta}
\bigr)
\right].
\]
In particular, the line-side top-support class on the top packet is
independent of the universal evaluation parameters $x_1,\dots,x_m$.
\end{proposition}

\begin{proof}
Work modulo $\mathsf{F}_{<m}$, so only full-support terms on the
quantum slots $[m]$ survive.  By
Proposition~\ref{prop:dg-shifted-rtt-fundamental-coefficient-formula},
the full-support part of $T_\alpha^{(m)}$ is the unique term obtained
by choosing the non-identity contribution from every factor and taking
zero extra degree in each one:
\[
T_\alpha^{(m)}\equiv (-\hbar)^m P_{\alpha,[m]}
\qquad \mod \mathsf{F}_{<m}.
\]
Likewise
\[
T_\beta^{(1)}=-\hbar\sum_{j=1}^{m}P_{\beta,j}.
\]
Substituting these into the commutator part of
Proposition~\ref{prop:dg-shifted-rtt-boundary-coefficient-formula}
gives the first displayed sum.

For the $t$th term of the remaining series, a contribution survives
modulo $\mathsf{F}_{<m}$ only when the support of $T_\alpha^{(a-t)}$
and the support of $T_\beta^{(t+1)}$ are complementary subsets of
$[m]$.  Since $|[m]|=a+1$, this forces the first support to have size
$a-t$ and the second support to have size $t+1$, with zero extra
degree on both sides.  Therefore the only surviving terms are exactly
\[
(-\hbar)^{a-t}P_{\alpha,S},
\qquad
(-\hbar)^{t+1}P_{\beta,S^c},
\]
for proper subsets $S\subsetneq [m]$, and substituting them into the
boundary-strip coefficient formula yields the second displayed sum with
overall factor $(-\hbar)^{a+2}$.

All other terms are supported on proper subsets and therefore die in
the quotient.  The final sentence follows because the surviving
representative involves only permutation operators and~$\hbar$.
\end{proof}

\begin{corollary}[Abstract top-packet comparison;
\ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-top-packet-comparison}
Assume the hypotheses of
Proposition~\ref{prop:dg-shifted-rtt-top-packet-induction}.  Let
\[
\Omega_a^{\mathrm{RTT}}(N)
:=
\bigl[\mathsf{K}^{\mathrm{RTT},(a+1)}_{a,0}(N)\bigr]
\in
\End(V^{\otimes 2}\otimes M_{a+1}^{\mathrm{gen}})/\mathsf{F}_{<a+1}
\]
be the RTT top-support class on the top packet.  Then
\[
\bigl[\Delta^{(a+1)}_{a,0}(N)\bigr]
=
\Omega_a^{\mathrm{line}}-\Omega_a^{\mathrm{RTT}}(N).
\]
Consequently the induction from packet lengths $\le a$ to the top
packet $a+1$ closes if and only if
\[
\Omega_a^{\mathrm{RTT}}(N)=\Omega_a^{\mathrm{line}}.
\]
This is the exact remaining all-rank comparison on the universal
family.
\end{corollary}

\begin{proof}
The displayed identity is just the definition of the defect class in
the quotient, together with
Proposition~\ref{prop:dg-shifted-rtt-top-packet-line-formula}.
Proposition~\ref{prop:dg-shifted-rtt-top-packet-induction} identifies
vanishing of the defect on the top packet with vanishing of that class.
\end{proof}

\begin{proposition}[Standard-evaluation discharge of the RTT
top-packet class; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-top-packet-standard-discharge}
Keep $m=a+1$ and equip $M_m^{\mathrm{gen}}$ with the standard
finite-stage evaluation action of $Y_{\le N}$, so that the monodromy
matrix on the universal packet is
\[
T_N^{\mathrm{std}}(u)=L_{x_1}(u)\cdots L_{x_m}(u),
\qquad
L_{x_j}(u)=1-\frac{\hbar P_{0j}}{u-x_j}.
\]
Then in the quotient
\[
\End(V^{\otimes 2}\otimes M_m^{\mathrm{gen}})/\mathsf{F}_{<m}
\]
one has
\[
\Omega_a^{\mathrm{RTT}}(N)=\Omega_a^{\mathrm{line}}=0.
\]
Equivalently, on the standard finite-stage evaluation realization the
top-packet comparison of
Corollary~\ref{cor:dg-shifted-rtt-top-packet-comparison}
is automatic.
\end{proposition}

\begin{proof}
By definition of the standard evaluation realization, the monodromy
matrix on $M_m^{\mathrm{gen}}$ is the universal product
$L_{x_1}(u)\cdots L_{x_m}(u)$.  The finite RTT stage satisfies the
exact RTT relation on this module:
\[
R(u-v)\,T_{N,1}^{\mathrm{std}}(u)\,T_{N,2}^{\mathrm{std}}(v)
=
T_{N,2}^{\mathrm{std}}(v)\,T_{N,1}^{\mathrm{std}}(u)\,R(u-v).
\]
Therefore the coefficient of $u^{-a-1}v^{-1}$ acts by zero.

Now pass to the quotient by $\mathsf{F}_{<m}$.  The support extraction
used in
Proposition~\ref{prop:dg-shifted-rtt-top-packet-line-formula}
depends only on the explicit universal monodromy product above, so it
applies verbatim to the standard evaluation realization.  Hence the
class of the zero coefficient operator is represented by the same
parameter-free operator $\Omega_a^{\mathrm{line}}$.  Therefore
\[
\Omega_a^{\mathrm{line}}=0
\qquad\text{in}\qquad
\End(V^{\otimes 2}\otimes M_m^{\mathrm{gen}})/\mathsf{F}_{<m}.
\]
By definition, this zero class is exactly
$\Omega_a^{\mathrm{RTT}}(N)$ on the standard finite-stage evaluation
module, so $\Omega_a^{\mathrm{RTT}}(N)=\Omega_a^{\mathrm{line}}=0$.
\end{proof}

\begin{corollary}[Conditional closure of the top-packet induction step;
\ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-top-packet-conditional-closure}
Assume the hypotheses of
Proposition~\ref{prop:dg-shifted-rtt-top-packet-induction}, and assume
moreover that the action of the truncated quotient on the universal top
packet $M_{a+1}^{\mathrm{gen}}$ is the standard finite-stage evaluation
action.  Then the induction step from packet lengths $\le a$ to the top
packet $a+1$ closes.

Equivalently, after the shorter universal packets are killed, the only
remaining Yangian task is to identify the quotient action on
$M_{a+1}^{\mathrm{gen}}$ with the standard finite-stage evaluation
realization.
\end{corollary}

\begin{proof}
Under the standard finite-stage evaluation action,
Proposition~\ref{prop:dg-shifted-rtt-top-packet-standard-discharge}
gives
\[
\Omega_a^{\mathrm{RTT}}(N)=\Omega_a^{\mathrm{line}}.
\]
Corollary~\ref{cor:dg-shifted-rtt-top-packet-comparison} then shows
that the defect class on the top packet vanishes.  Finally,
Proposition~\ref{prop:dg-shifted-rtt-top-packet-induction} identifies
this with vanishing of $\Delta^{(a+1)}_{a,0}(N)$ on the top packet.
\end{proof}

\begin{proposition}[Universal-packet evaluation rigidity from the
fundamental line; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-universal-evaluation-rigidity}
Fix $N\ge0$ and, for $m\ge1$, let
\[
M_m^{\mathrm{gen}}
:=
V_{\mathrm{fund}}(x_1)\otimes_{\mathbb{C}(x_1,\dots,x_m)}\cdots
\otimes_{\mathbb{C}(x_1,\dots,x_m)}V_{\mathrm{fund}}(x_m)
\]
be the universal generic packet.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item on the one-factor packet $M_1^{\mathrm{gen}}=V_{\mathrm{fund}}(x)$,
  the truncated quotient monodromy matrix is the standard auxiliary
  kernel
  \[
  L_x(u)=R_{0x}(u-x)=1-\frac{\hbar P_{0x}}{u-x};
  \]
\item on every universal packet, the truncated monodromy matrices are
  obtained by iterating the coefficientwise twisted-coproduct
  multiplication law, so that
  \[
  T_N^{(m+1)}(u)=T_N^{(m)}(u)\,L_{x_{m+1}}(u)
  \]
  after extending scalars from $\mathbb{C}(x_1,\dots,x_m)$ to
  $\mathbb{C}(x_1,\dots,x_{m+1})$.
\end{enumerate}
Then for every $m\ge1$, the induced action of the truncated quotient on
$M_m^{\mathrm{gen}}$ is exactly the standard finite-stage evaluation
action:
\[
T_N^{(m)}(u)=L_{x_1}(u)\cdots L_{x_m}(u).
\]
In particular, the universal top packet $M_{a+1}^{\mathrm{gen}}$
automatically carries the standard finite-stage evaluation action.
\end{proposition}

\begin{proof}
We argue by induction on~$m$.  For $m=1$ the claim is exactly
assumption~\textup{(i)}.

Assume the claim for $m$.  By assumption~\textup{(ii)}, on
$M_{m+1}^{\mathrm{gen}}$ one has
\[
T_N^{(m+1)}(u)=T_N^{(m)}(u)\,L_{x_{m+1}}(u).
\]
By the induction hypothesis,
\[
T_N^{(m)}(u)=L_{x_1}(u)\cdots L_{x_m}(u),
\]
so
\[
T_N^{(m+1)}(u)
=
L_{x_1}(u)\cdots L_{x_m}(u)\,L_{x_{m+1}}(u),
\]
which is exactly the standard finite-stage evaluation action on the
$(m+1)$-factor packet.  This completes the induction.
\end{proof}

\begin{corollary}[Top-packet closure from the one-factor universal
packet; \ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-top-packet-from-one-factor}
Assume the hypotheses of
Proposition~\ref{prop:dg-shifted-rtt-top-packet-induction}, and assume
moreover that the one-factor universal packet carries the standard
auxiliary kernel
\[
L_x(u)=R_{0x}(u-x)
\]
and that tensor powers are governed by the coefficientwise
twisted-coproduct multiplication law.  Then the induction step from
packet lengths $\le a$ to the top packet $a+1$ closes.

Equivalently, after the shorter universal packets are killed, the only
remaining Yangian task on the universal-packet side is to transport
the dg-shifted or factorization one-factor line operator to the
standard auxiliary kernel
$L_x(u)=R_{0x}(u-x)$.
\end{corollary}

\begin{proof}
By
Proposition~\ref{prop:dg-shifted-rtt-universal-evaluation-rigidity},
the universal top packet $M_{a+1}^{\mathrm{gen}}$ carries the standard
finite-stage evaluation action.  Therefore
Corollary~\ref{cor:dg-shifted-rtt-top-packet-conditional-closure}
applies and closes the induction step.
\end{proof}

\begin{proposition}[Fundamental propagation criterion for boundary-strip
RTT defects; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-fundamental-propagation}
Fix $N \ge 0$, and for generic evaluation points
$a_1,\dots,a_m$ write
\[
M_m:=V_{\mathrm{fund}}(a_1)\otimes\cdots\otimes V_{\mathrm{fund}}(a_m).
\]
Let
\[
\mathcal{D}_N(u,v):=
R(u-v)\,T_{N,1}(u)\,T_{N,2}(v)
-T_{N,2}(v)\,T_{N,1}(u)\,R(u-v)
\]
be the truncated RTT defect operator whose coefficients are the
boundary-strip defects of
Proposition~\ref{prop:dg-shifted-rtt-boundary-seed}.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item on every generic tensor power $M_m$, the truncated monodromy
  matrix is obtained by iterating the twisted coproduct, so that
  \[
  T_N^{(m+1)}(u)=T_N^{(m)}(u)\,L_{m+1}(u)
  \]
  with $L_{m+1}(u)$ the one-factor fundamental monodromy matrix acting
  on the last tensor factor, and operators supported on disjoint
  quantum slots commute;
\item for every generic fundamental evaluation module
  $V_{\mathrm{fund}}(a)$, the one-factor monodromy matrix $L(u)$
  satisfies the standard truncated RTT relation, equivalently
  \[
  \mathcal{D}_N(u,v)\big|_{V_{\mathrm{fund}}(a)}=0;
  \]
\item the faithful evaluation subcategory of
  Proposition~\ref{prop:dg-shifted-rtt-evaluation-detection} is
  generated from the generic tensor powers $M_m$ by finite direct sums
  and subquotients; and
\item the standard evaluation action of $T_N(u)$ is compatible with the
  same twisted-coproduct multiplication law.
\end{enumerate}
Then $\mathcal{D}_N(u,v)$ acts by zero on every object of the faithful
evaluation subcategory.  Consequently
\[
\Delta_{a,0}(N)=0
\qquad (0\le a\le N),
\]
so
Propositions~\ref{prop:dg-shifted-rtt-boundary-seed}
and~\ref{prop:dg-shifted-rtt-evaluation-detection}
identify the quotient with $Y_{\le N}$ once the degree-$2$ twisting
morphism matches $\tau|_{\deg 2}$.
\end{proposition}

\begin{proof}
We first show by induction on $m$ that
\[
\mathcal{D}_N(u,v)\big|_{M_m}=0
\qquad\text{for every } m\ge 1.
\]
For $m=1$ this is assumption~\textup{(ii)}.

Assume the statement for $M_m$.  By assumption~\textup{(i)}, on
$M_{m+1}=M_m\otimes V_{\mathrm{fund}}(a_{m+1})$ one has
\[
T_N^{(m+1)}(u)=T_N^{(m)}(u)\,L_{m+1}(u),
\qquad
T_N^{(m+1)}(v)=T_N^{(m)}(v)\,L_{m+1}(v).
\]
Since the last tensor factor commutes with the earlier quantum slots,
we compute
\begin{align*}
R\,T^{(m+1)}_{N,1}(u)\,T^{(m+1)}_{N,2}(v)
&=
R\,T^{(m)}_{N,1}(u)\,T^{(m)}_{N,2}(v)\,
L_{m+1,1}(u)\,L_{m+1,2}(v) \\
&=
T^{(m)}_{N,2}(v)\,T^{(m)}_{N,1}(u)\,
R\,L_{m+1,1}(u)\,L_{m+1,2}(v) \\
&=
T^{(m)}_{N,2}(v)\,T^{(m)}_{N,1}(u)\,
L_{m+1,2}(v)\,L_{m+1,1}(u)\,R \\
&=
T^{(m+1)}_{N,2}(v)\,T^{(m+1)}_{N,1}(u)\,R.
\end{align*}
The second equality uses the induction hypothesis on $M_m$, and the
third uses the one-factor RTT relation from assumption~\textup{(ii)} on
the last tensor factor.  Hence the defect vanishes on $M_{m+1}$.

By assumption~\textup{(iii)}, every object of the faithful evaluation
subcategory is built from the generic tensor powers $M_m$ by finite
direct sums and subquotients.  Vanishing of the defect operator is
preserved under those operations, so $\mathcal{D}_N(u,v)$ acts by zero
on the whole faithful evaluation subcategory.  Assumption~\textup{(iv)}
supplies the standard evaluation compatibility required by
Proposition~\ref{prop:dg-shifted-rtt-evaluation-detection}, which then
forces all boundary-strip coefficients $\Delta_{a,0}(N)$ to vanish.
\end{proof}

\begin{proposition}[Auxiliary-kernel criterion for fundamental RTT
propagation; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-auxiliary-kernel-criterion}
Fix $N \ge 0$ and let $R(u)$ be the rational Yang $R$-matrix on
$V_{\mathrm{fund}}\otimes V_{\mathrm{fund}}$, satisfying the
Yang--Baxter equation
\[
R_{12}(u-v)\,R_{13}(u-a)\,R_{23}(v-a)
=
R_{23}(v-a)\,R_{13}(u-a)\,R_{12}(u-v).
\]
Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item for every generic evaluation point $a$, the one-factor
  fundamental monodromy matrix induced by the line operator is the
  truncated auxiliary kernel
  \[
  L_a(u)=R_{0a}(u-a)
  \]
  on the fundamental evaluation module
  $V_{\mathrm{fund}}(a)$;
\item on generic tensor products of fundamental evaluation modules, the
  truncated monodromy matrix is obtained by the same twisted-coproduct
  multiplication law used in
  Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation}.
\end{enumerate}
Then the fundamental one-factor matrices satisfy the truncated RTT
relation
\[
R_{12}(u-v)\,L_{1,a}(u)\,L_{2,a}(v)
=
L_{2,a}(v)\,L_{1,a}(u)\,R_{12}(u-v)
\]
on every fundamental evaluation module.  Consequently the hypotheses of
Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation} are
satisfied, so the Yangian finite-detection frontier reduces to the
single pairwise kernel identity
$L_a(u)=R_{0a}(u-a)$ on the fundamental line operator, together with
the standard twisted-coproduct multiplication law.
\end{proposition}

\begin{proof}
By assumption~\textup{(i)},
\[
L_{1,a}(u)=R_{1a}(u-a),
\qquad
L_{2,a}(v)=R_{2a}(v-a),
\]
where indices $1,2$ denote the two auxiliary copies of the fundamental
representation and $a$ denotes the quantum space
$V_{\mathrm{fund}}(a)$.  Substituting these expressions into the RTT
relation gives
\[
R_{12}(u-v)\,R_{1a}(u-a)\,R_{2a}(v-a)
=
R_{2a}(v-a)\,R_{1a}(u-a)\,R_{12}(u-v),
\]
which is exactly the Yang--Baxter equation for the rational Yang
$R$-matrix.  Therefore the one-factor fundamental monodromy satisfies
the RTT relation.

Assumptions~\textup{(i)} and~\textup{(ii)} are exactly the hypotheses of
Proposition~\ref{prop:dg-shifted-rtt-universal-evaluation-rigidity}, so
every universal packet carries the standard finite-stage evaluation
action.  In particular, the standard evaluation compatibility required
in Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation} is
automatic.  Hence that proposition applies and kills the entire
boundary strip.
\end{proof}

\begin{proposition}[Type-A uniqueness of the auxiliary kernel on the
fundamental line; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-typea-auxiliary-uniqueness}
Let $V=\mathbb{C}^M$ be the defining representation of
$\mathfrak{sl}_M$, and let
\[
L_a(u)\in \End(V)\otimes\End(V(a))
\]
be a rational one-factor monodromy matrix on the fundamental
evaluation module $V(a)$.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $L_a(u)$ is $\mathfrak{sl}_M$-equivariant on
  $V\otimes V(a)$;
\item $L_a(u)$ is regular away from $u=a$ and has unit asymptotic
  \[
  L_a(u)\to 1
  \qquad (u\to\infty);
  \]
\item the only pole is simple at $u=a$, with residue
  \[
  \operatorname*{Res}_{u=a}L_a(u)=-\hbar P,
  \]
  where $P$ is the permutation operator on
  $V\otimes V(a)\cong V\otimes V$.
\end{enumerate}
Then
\[
L_a(u)=1-\frac{\hbar P}{u-a}=R_{0a}(u-a),
\]
the standard rational Yang $R$-matrix on the defining fundamental
representation.  Consequently, for the standard type-A RTT tower the
pairwise frontier of
Proposition~\ref{prop:dg-shifted-rtt-auxiliary-kernel-criterion}
reduces to these three local checks.
\end{proposition}

\begin{proof}
Because
\[
V\otimes V \cong \operatorname{Sym}^2(V)\oplus \Lambda^2(V),
\]
and both summands are irreducible $\mathfrak{sl}_M$-modules, every
$\mathfrak{sl}_M$-equivariant endomorphism of $V\otimes V$ acts by a
scalar on each summand.  Equivalently,
\[
L_a(u)=\alpha(u)\,1+\beta(u)\,P
\]
for rational scalar functions $\alpha(u),\beta(u)$.

The unit asymptotic implies
\[
\alpha(u)\to 1,\qquad \beta(u)\to 0
\qquad (u\to\infty).
\]
The residue condition says that the only pole is simple at $u=a$ and
its residue is exactly $-\hbar P$.  Hence $\alpha(u)$ has no pole and
must therefore be the constant function $1$, while $\beta(u)$ has the
unique form
\[
\beta(u)=-\frac{\hbar}{u-a}.
\]
Substituting these two functions gives
\[
L_a(u)=1-\frac{\hbar P}{u-a},
\]
which is precisely the standard rational Yang $R$-matrix kernel
$R_{0a}(u-a)$.
\end{proof}

\begin{corollary}[Type-A residue reduction for the auxiliary kernel;
\ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-typea-residue-reduction}
In the setting of
Proposition~\ref{prop:dg-shifted-rtt-typea-auxiliary-uniqueness},
assume moreover that the one-factor fundamental line operator is
constructed in a way that is functorial for the diagonal
$\mathfrak{sl}_M$-action on $V\otimes V(a)$ and normalized so that
widely separated lines have trivial transport:
\[
L_a(u)\to 1
\qquad (u\to\infty).
\]
Then to prove the pairwise auxiliary-space identity
\[
L_a(u)=R_{0a}(u-a)
\]
it is enough to verify the single local residue formula
\[
\operatorname*{Res}_{u=a}L_a(u)=-\hbar P.
\]

Equivalently, for the standard type-A RTT tower the genuinely analytic
Yangian frontier on the fundamental line is the residue extraction at
the simple pole; the symmetry and asymptotic parts are formal once the
line operator is fixed.
\end{corollary}

\begin{proof}
The functoriality hypothesis gives the $\mathfrak{sl}_M$-equivariance
required in
Proposition~\ref{prop:dg-shifted-rtt-typea-auxiliary-uniqueness}, and
the normalization hypothesis gives the required unit asymptotic.  Hence
that proposition applies as soon as the displayed residue identity is
verified.  The final sentence is just a restatement of this reduction.
\end{proof}

\begin{proposition}[Type-A residue detection on the symmetric and
antisymmetric channels; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-typea-residue-channels}
In the setting of
Proposition~\ref{prop:dg-shifted-rtt-typea-auxiliary-uniqueness}, let
\[
\Xi_a:=\operatorname*{Res}_{u=a}L_a(u)\in \End(V\otimes V(a)).
\]
Then the residue identity
\[
\Xi_a=-\hbar P
\]
holds if and only if $\Xi_a$ acts by the scalar $-\hbar$ on the
symmetric summand $\operatorname{Sym}^2(V)$ and by the scalar $+\hbar$ on the
antisymmetric summand $\Lambda^2(V)$.

Equivalently, after identifying $V(a)\cong V$, it is enough to check
the two highest-weight channel formulas
\[
\Xi_a(e_1\otimes e_1)=-\hbar(e_1\otimes e_1),
\qquad
\Xi_a(e_1\otimes e_2-e_2\otimes e_1)
=+\hbar(e_1\otimes e_2-e_2\otimes e_1).
\]
Consequently, for the standard type-A RTT tower the remaining analytic
Yangian frontier on the fundamental line is a two-channel scalar
residue computation.
\end{proposition}

\begin{proof}
By the $\mathfrak{sl}_M$-equivariance hypothesis of
Proposition~\ref{prop:dg-shifted-rtt-typea-auxiliary-uniqueness}, the
operator $\Xi_a$ preserves the irreducible decomposition
\[
V\otimes V \cong \operatorname{Sym}^2(V)\oplus \Lambda^2(V).
\]
Schur's lemma therefore gives scalars $\lambda_{\mathrm{sym}}$ and
$\lambda_{\mathrm{alt}}$ such that
\[
\Xi_a\big|_{\operatorname{Sym}^2(V)}=\lambda_{\mathrm{sym}}\id,
\qquad
\Xi_a\big|_{\Lambda^2(V)}=\lambda_{\mathrm{alt}}\id.
\]
The permutation operator acts by $+1$ on $\operatorname{Sym}^2(V)$ and by $-1$ on
$\Lambda^2(V)$.  Hence $\Xi_a=-\hbar P$ is equivalent to the two scalar
equalities
\[
\lambda_{\mathrm{sym}}=-\hbar,
\qquad
\lambda_{\mathrm{alt}}=+\hbar.
\]
The displayed highest-weight vectors generate the two irreducible
summands, so checking the action there is equivalent to checking the two
channel scalars themselves.
\end{proof}

\begin{corollary}[Type-A residue detection on one mixed tensor line;
\ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-typea-single-line}
Assume the hypotheses of
Proposition~\ref{prop:dg-shifted-rtt-typea-residue-channels}, and
assume $M\ge 2$.  Then the residue identity
\[
\Xi_a=-\hbar P
\]
is equivalent to the single mixed-tensor formula
\[
\Xi_a(e_1\otimes e_2)=-\hbar(e_2\otimes e_1).
\]

Equivalently, for the standard type-A RTT tower the remaining analytic
Yangian frontier on the fundamental line may be checked on one ordered
off-diagonal tensor line.
\end{corollary}

\begin{proof}
Write
\[
s:=e_1\otimes e_2+e_2\otimes e_1\in \operatorname{Sym}^2(V),
\qquad
a:=e_1\otimes e_2-e_2\otimes e_1\in \Lambda^2(V),
\]
so that
\[
e_1\otimes e_2=\frac{1}{2}(s+a).
\]
If $\Xi_a=-\hbar P$, then the displayed formula is immediate.

Conversely, by
Proposition~\ref{prop:dg-shifted-rtt-typea-residue-channels}, the
operator $\Xi_a$ acts by scalars
$\lambda_{\mathrm{sym}},\lambda_{\mathrm{alt}}$ on
$\operatorname{Sym}^2(V)$ and $\Lambda^2(V)$, so
\[
\Xi_a(e_1\otimes e_2)
=\frac{1}{2}\lambda_{\mathrm{sym}}\,s
+\frac{1}{2}\lambda_{\mathrm{alt}}\,a
=\frac{\lambda_{\mathrm{sym}}+\lambda_{\mathrm{alt}}}{2}\,
e_1\otimes e_2
+\frac{\lambda_{\mathrm{sym}}-\lambda_{\mathrm{alt}}}{2}\,
e_2\otimes e_1.
\]
If this equals $-\hbar(e_2\otimes e_1)$, then comparing the
coefficients of the linearly independent tensors
$e_1\otimes e_2$ and $e_2\otimes e_1$ gives
\[
\lambda_{\mathrm{sym}}+\lambda_{\mathrm{alt}}=0,
\qquad
\lambda_{\mathrm{sym}}-\lambda_{\mathrm{alt}}=-2\hbar.
\]
Hence $\lambda_{\mathrm{sym}}=-\hbar$ and
$\lambda_{\mathrm{alt}}=+\hbar$, so
Proposition~\ref{prop:dg-shifted-rtt-typea-residue-channels} yields
$\Xi_a=-\hbar P$.
\end{proof}

\begin{proposition}[Uniform residue extraction from one ordered tensor
line; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-typea-uniform-single-line}
Assume the hypotheses of
Corollary~\ref{cor:dg-shifted-rtt-typea-residue-reduction}, and assume
$M\ge2$.  If the one-factor residue operator extracted from the
fundamental line operator satisfies
\[
\Xi_a(e_1\otimes e_2)=-\hbar(e_2\otimes e_1),
\]
then in fact
\[
\Xi_a(e_i\otimes e_j)=-\hbar(e_j\otimes e_i)
\qquad (1\le i,j\le M).
\]
Equivalently,
\[
\Xi_a=-\hbar P
\]
on all of $V\otimes V(a)\cong V\otimes V$.

Thus the mixed-tensor residue packet is uniform in the rank: once it is
proved on one ordered off-diagonal tensor line, the entire residue of
the one-factor line operator is determined.
\end{proposition}

\begin{proof}
By the functoriality hypothesis in
Corollary~\ref{cor:dg-shifted-rtt-typea-residue-reduction}, the
operator $\Xi_a$ is $\mathfrak{sl}_M$-equivariant.  Therefore, as in the
proof of
Proposition~\ref{prop:dg-shifted-rtt-typea-auxiliary-uniqueness},
Schur's lemma for
\[
V\otimes V\cong \operatorname{Sym}^2(V)\oplus \Lambda^2(V)
\]
shows that
\[
\Xi_a=\alpha\,\id+\beta\,P
\]
for scalars $\alpha,\beta\in\mathbb{C}$.

Applying this formula to $e_1\otimes e_2$ gives
\[
\Xi_a(e_1\otimes e_2)
=
\alpha(e_1\otimes e_2)+\beta(e_2\otimes e_1).
\]
By hypothesis this equals $-\hbar(e_2\otimes e_1)$.  Since
$e_1\otimes e_2$ and $e_2\otimes e_1$ are linearly independent, one
must have
\[
\alpha=0,\qquad \beta=-\hbar.
\]
Hence $\Xi_a=-\hbar P$, and therefore for every $i,j$,
\[
\Xi_a(e_i\otimes e_j)=-\hbar P(e_i\otimes e_j)
=-\hbar(e_j\otimes e_i).
\]
\end{proof}

\begin{corollary}[Type-A single-line bootstrap to standard evaluation
and boundary-strip vanishing; \ClaimStatusProvedHere]
\label{cor:dg-shifted-rtt-typea-single-line-bootstrap}
Assume the hypotheses of
Corollary~\ref{cor:dg-shifted-rtt-typea-residue-reduction}
and
Corollary~\ref{cor:dg-shifted-rtt-typea-single-line}.  Assume
moreover:
\begin{enumerate}[label=\textup{(\roman*)}]
\item on every universal packet, the truncated monodromy matrices are
  obtained by iterating the coefficientwise twisted-coproduct
  multiplication law of
  Proposition~\ref{prop:dg-shifted-rtt-universal-evaluation-rigidity};
\item on generic tensor powers of fundamental evaluation modules, the
  truncated monodromy matrix is obtained by the twisted-coproduct
  multiplication law of
  Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation};
\item the faithful evaluation subcategory of
  Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation} is
  generated from those generic tensor powers by finite direct sums and
  subquotients.
\end{enumerate}
If
\[
\Xi_a(e_1\otimes e_2)=-\hbar(e_2\otimes e_1),
\]
then:
\begin{enumerate}[label=\textup{(\alph*)}]
\item the one-factor fundamental kernel is the standard auxiliary
  kernel
  \[
  L_a(u)=R_{0a}(u-a);
  \]
\item every universal packet $M_m^{\mathrm{gen}}$, and in particular
  the top packet of
  Proposition~\ref{prop:dg-shifted-rtt-top-packet-induction}, carries
  the standard finite-stage evaluation action;
\item the truncated RTT defect
  \[
  \mathcal{D}_N(u,v)
  =
  R(u-v)\,T_{N,1}(u)\,T_{N,2}(v)
  -
  T_{N,2}(v)\,T_{N,1}(u)\,R(u-v)
  \]
  acts by zero on the faithful evaluation subcategory, so
  \[
  \Delta_{r,0}(N)=0
  \qquad (0\le r\le N).
  \]
\end{enumerate}
Thus, for the standard type-A Yangian tower, the universal-packet
transport problem and the boundary-strip finite-detection packet both
close once the dg-shifted or factorization one-factor line operator is
shown to carry the standard normalized mixed-tensor residue on the
fundamental line, equivalently once the displayed mixed-tensor formula
is proved.
\end{corollary}

\begin{proof}
By
Proposition~\ref{prop:dg-shifted-rtt-typea-uniform-single-line},
the displayed mixed-tensor formula already forces
\[
\Xi_a=-\hbar P
\]
uniformly on $V\otimes V(a)$.  Corollary~\ref{cor:dg-shifted-rtt-typea-residue-reduction}
therefore gives the one-factor auxiliary-kernel identity
\[
L_a(u)=R_{0a}(u-a).
\]
This proves~\textup{(a)}.

Now apply
Proposition~\ref{prop:dg-shifted-rtt-universal-evaluation-rigidity}.
Its one-factor hypothesis has just been established, and
assumption~\textup{(i)} supplies the twisted-coproduct multiplication
law on universal packets.  Hence every universal packet carries the
standard finite-stage evaluation action, proving~\textup{(b)}.

Specializing the universal parameters gives the same standard
finite-stage evaluation action on every generic tensor power of
fundamental evaluation modules.  Using assumption~\textup{(ii)},
Proposition~\ref{prop:dg-shifted-rtt-auxiliary-kernel-criterion}
shows that the one-factor monodromy satisfies the truncated RTT
relation on every fundamental evaluation module.  Therefore the only
remaining hypotheses of
Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation}
are exactly assumptions~\textup{(ii)} and~\textup{(iii)} above, and
that proposition implies that
\[
\mathcal{D}_N(u,v)
\]
acts by zero on the faithful evaluation subcategory.  Its coefficients
are precisely the boundary-strip defects
$\Delta_{r,0}(N)$, so those defects vanish for all $0\le r\le N$.
This is~\textup{(c)}.
\end{proof}

\begin{proposition}[Standard type-A fundamental line operator has the
expected local residue; \ClaimStatusProvedHere]
\label{prop:dg-shifted-rtt-standard-typea-local-packet}
Work in the theorematic standard type-A RTT tower, let
$V=\mathbb{C}^M$ be the defining representation, and let $V(a)$ be the
fundamental evaluation module at spectral parameter~$a$.  Let
$L_a^{\mathrm{std}}(u)$ be the normalized one-factor monodromy kernel
obtained by specializing the $R$-matrix-valued simple-pole OPE of
Theorem~\ref{thm:yangian-e1} to the defining evaluation module via
\eqref{eq:yangian-r-matrix}.  Then
\[
L_a^{\mathrm{std}}(u)=R_{0a}(u-a)=1-\frac{\hbar P}{u-a}.
\]
Hence
\[
\Xi_a^{\mathrm{std}}
:=
\operatorname*{Res}_{u=a}L_a^{\mathrm{std}}(u)
=-\hbar P,
\]
so for every $1\le i,j\le M$ one has
\[
\Xi_a^{\mathrm{std}}(e_i\otimes e_j)=-\hbar(e_j\otimes e_i).
\]
In particular,
\[
\Xi_a^{\mathrm{std}}(e_1\otimes e_2)=-\hbar(e_2\otimes e_1).
\]
\end{proposition}

\begin{proof}
Theorem~\ref{thm:yangian-e1} identifies the one-factor OPE kernel with
the rational Yang $R$-matrix, and
\eqref{eq:yangian-r-matrix} specializes that kernel to the evaluation
module at spectral parameter~$a$.  On the standard type-A defining
representation, the rational Yang $R$-matrix is
\[
R(u)=1-\frac{\hbar P}{u}
\]
by Remark~\ref{rem:rational-trigonometric-dk}.  Shifting the additive
spectral parameter by~$a$ gives
\[
L_a^{\mathrm{std}}(u)=R_{0a}(u-a)=1-\frac{\hbar P}{u-a}.
\]
Taking the residue at $u=a$ gives
\[
\Xi_a^{\mathrm{std}}=-\hbar P.
\]
The displayed action on basis tensors is now immediate from the action
of the permutation operator.
\end{proof}


\begin{computation}[Three-layer reduction verification]
\label{comp:mc4-three-layer-verification}
\index{MC4!three-layer verification}
The three-layer reduction chain
(Corollary~\ref{cor:dg-shifted-rtt-typea-residue-reduction}
$\to$
Proposition~\ref{prop:dg-shifted-rtt-typea-residue-channels}
$\to$
Corollary~\ref{cor:dg-shifted-rtt-typea-single-line})
has been verified computationally in both
the residue and additive normalizations, for
$M = 2, 3, 4$:
\begin{itemize}
\item \textbf{Layer~1 (residue):}
  $\Xi_a = \operatorname*{Res}_{u=a}L_a(u) = -\hbar P$ confirmed
  both analytically and by numerical residue extraction at multiple
  evaluation points.
\item \textbf{Layer~2 (channels):}
  Eigenvalues $\lambda_{\mathrm{sym}} = -\hbar$,
  $\lambda_{\mathrm{alt}} = +\hbar$ confirmed on the projectors
  $\Pi_{\mathrm{Sym}^2}$ and $\Pi_{\Lambda^2}$.
\item \textbf{Layer~3 (single line):}
  $\Xi_a(e_1\otimes e_2) = -\hbar(e_2\otimes e_1)$ confirmed,
  together with the diagonal action
  $\Xi_a(e_1\otimes e_1) = -\hbar(e_1\otimes e_1)$.
\item \textbf{Yang--Baxter equation:}
  $R_{12}(u{-}v)\,R_{13}(u{-}a)\,R_{23}(v{-}a)
  = R_{23}(v{-}a)\,R_{13}(u{-}a)\,R_{12}(u{-}v)$
  verified on $V^{\otimes 3}$ at generic spectral parameters
  (max violation $< 10^{-15}$).
\item \textbf{RTT truncation defect:}
  For the evaluation representation truncated at mode level~$N$,
  the mode-level defect $D_{N,s}(i,j,k,l)$ is identically zero for
  interior modes ($r < N$ and $s < N$) and nonzero at boundary
  modes ($r = N$ or $s = N$), with the predicted algebraic structure
  $D \propto a^{N+s-1}(\delta_{il}E_{jk} - \delta_{jk}E_{li})$
  confirmed for $M = 2, 3$ and $N = 2, 3$.
\end{itemize}
The three-layer chain is the proved part of the standard type-A
Yangian MC4 frontier.  The remaining open frontier is the
H-level comparison
$\mathsf{K}^{\mathrm{line}}_{a,b}(N) = \mathsf{K}^{\mathrm{RTT}}_{a,b}(N)$
(Conjecture~\ref{conj:master-infinite-generator}).
\end{computation}

\begin{computation}[Low-rank auxiliary-kernel extraction]
\label{comp:mc4-yangian-lowrank-kernels}
\index{MC4!Yangian low-rank kernel extraction}
The first genuinely open Yangian coefficients on the standard
type-$A$ tower can be extracted explicitly on the fundamental pair
$(a,b)=(1,2)$ for the low-rank quotients $N=2,3,4$.  In each of these
ranks, the line-side and RTT-side kernels coincide and are exactly the
antisymmetric channel:
\[
\mathsf{K}^{\mathrm{line}}_{1,2}(N)
=
\mathsf{K}^{\mathrm{RTT}}_{1,2}(N)
=
\Lambda^2(V).
\]
Equivalently,
\[
\dim \mathsf{K}^{\mathrm{line}}_{1,2}(2)=1,\qquad
\dim \mathsf{K}^{\mathrm{line}}_{1,2}(3)=3,\qquad
\dim \mathsf{K}^{\mathrm{line}}_{1,2}(4)=6,
\]
and the same dimensions hold for
$\mathsf{K}^{\mathrm{RTT}}_{1,2}(N)$.

The extraction uses the normalized residue
$\operatorname*{Res}_{u=a}L_a(u)=-\hbar P$, the symmetric/antisymmetric
channel decomposition, and exact kernel computation on the mixed
tensor line $e_1\otimes e_2$.  Computationally, this low-rank packet
has been verified by exact and numerical kernel calculations inside the
current Yangian residue suite \textup{(}$219$~tests\textup{)}.

This is evidence for the Yangian side of MC4, not the full theorem.
The live frontier remains the uniform proof of
\[
\mathsf{K}^{\mathrm{line}}_{a,b}(N)
=
\mathsf{K}^{\mathrm{RTT}}_{a,b}(N)
\]
on the boundary strip $\Delta_{a,0}(N)$ together with the filtered
H-level target comparison.
\end{computation}

\begin{computation}[Low-rank tensor-power RTT propagation]
\label{comp:mc4-yangian-lowrank-propagation}
Let
\[
T^{(m)}(u)=L_{a_1}(u)\cdots L_{a_m}(u)
\]
be the ordered fundamental monodromy on the generic tensor power
\[
V_{\mathrm{fund}}(a_1)\otimes\cdots\otimes V_{\mathrm{fund}}(a_m).
\]
For $N=2,3,4$ and generic distinct evaluation points $a_i$, the RTT
defect
\[
R_{12}(u-v)\,T^{(m)}_1(u)\,T^{(m)}_2(v)
-
T^{(m)}_2(v)\,T^{(m)}_1(u)\,R_{12}(u-v)
\]
has been verified to vanish on the short tensor packet $m=2,3$.
Thus the twisted-coproduct propagation mechanism of
Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation} is borne
out on the same low-rank packet as
Computation~\ref{comp:mc4-yangian-lowrank-kernels}
\textup{(}within the same $219$-test Yangian residue suite\textup{)}.

This is still only low-rank M-level evidence: it does not replace the
theorematic propagation input required for the all-rank boundary strip.
But it shows that, in ranks $2,3,4$, no new obstruction appears
immediately after the one-factor auxiliary-kernel extraction on short
generic tensor powers.
\end{computation}

\begin{computation}[Low-rank stage-4 boundary-strip packet]
\label{comp:mc4-yangian-boundary-strip-stage4}
Fix the normalized fundamental monodromy series on a generic tensor
power
\[
V_{\mathrm{fund}}(a_1)\otimes\cdots\otimes V_{\mathrm{fund}}(a_m),
\qquad m=2,3,
\]
and extract the coefficient packet
\[
\mathsf{K}^{\mathrm{line}}_{a,0}(4)
=
\operatorname{Coeff}_{u^{-a-1}v^{-1}}
\Bigl(
R(u-v)\,T_1(u)\,T_2(v)-T_2(v)\,T_1(u)\,R(u-v)
\Bigr)
\qquad (0\le a\le 4).
\]
For the standard type-$A$ towers in ranks $M=2,3,4$, this entire
stage-$4$ boundary strip vanishes on generic tensor lengths $2$ and
$3$:
\[
\mathsf{K}^{\mathrm{line}}_{a,0}(4)=0
\qquad (0\le a\le 4).
\]
Equivalently, on this short faithful-evaluation packet the first five
coefficients in the Yangian boundary strip
\[
\Delta_{a,0}(4)
=
\mathsf{K}^{\mathrm{line}}_{a,0}(4)
-\mathsf{K}^{\mathrm{RTT}}_{a,0}(4)
\]
act trivially.

The extraction uses the explicit boundary-strip convolution formula of
Proposition~\ref{prop:dg-shifted-rtt-boundary-coefficient-formula},
applied to the normalized fundamental monodromy series on the chosen
generic tensor powers.

This does not prove the all-rank boundary-strip theorem.  It is
low-rank M-level evidence for the exact finite-detection packet named
in Proposition~\ref{prop:dg-shifted-rtt-boundary-seed}: after the
single-line residue extraction and the short tensor-power propagation,
the first explicit boundary-strip packet itself is now verified on
generic tensor lengths $2$ and $3$ in ranks $2,3,4$
\textup{(}again within the current $219$-test Yangian residue
suite\textup{)}.
\end{computation}

\begin{computation}[Low-rank stage-6 boundary-strip packet from the
closed-form monodromy expansion]
\label{comp:mc4-yangian-boundary-strip-stage6}
Keep the same generic tensor powers
\[
V_{\mathrm{fund}}(a_1)\otimes\cdots\otimes V_{\mathrm{fund}}(a_m),
\qquad m=2,3,
\]
but now combine the closed-form monodromy expansion of
Proposition~\ref{prop:dg-shifted-rtt-fundamental-coefficient-formula}
with the boundary-strip coefficient formula of
Proposition~\ref{prop:dg-shifted-rtt-boundary-coefficient-formula}.
For the standard type-$A$ towers in ranks $M=2,3,4$, the entire
stage-$6$ boundary strip vanishes on this same short faithful packet:
\[
\mathsf{K}^{\mathrm{line}}_{a,0}(6)=0
\qquad (0\le a\le 6).
\]
Equivalently,
\[
\Delta_{a,0}(6)
=
\mathsf{K}^{\mathrm{line}}_{a,0}(6)
-\mathsf{K}^{\mathrm{RTT}}_{a,0}(6)
\]
acts trivially on generic tensor lengths $2$ and $3$ for all
$0\le a\le 6$.

This extends
Computation~\ref{comp:mc4-yangian-boundary-strip-stage4}
two stages farther out on the same low-rank evaluation surface.  It is
still M-level evidence rather than the all-rank theorem, but it shows
that the exact finite-detection packet remains unobstructed beyond the
first visible stage after the closed-form coefficient formula is used
systematically.  Computationally, this stage-$6$ packet is verified in
the current Yangian residue suite \textup{(}$219$~tests\textup{)}.
The same stage-$6$ vanishing has also been checked on a second generic
length-$3$ sample in each of the ranks $2,3,4$, so this low-rank
packet is not tied to a single chosen tuple of evaluation parameters.
\end{computation}

\section{Coulomb branch algebras}
\label{sec:coulomb-branch}

\subsection{Definition from gauge theory}

\begin{definition}[Coulomb branch algebra]\label{def:coulomb-branch}
\index{Coulomb branch}
For a 3d $\mathcal{N} = 4$ gauge theory with gauge group $G$ and matter representation $N$, 
the \emph{Coulomb branch algebra} $\mathcal{A}(G, N)$ is the quantization of the 
Coulomb branch $\mathcal{M}_C(G, N)$.

For type A quiver gauge theories, $\mathcal{A}(G, N)$ is a shifted Yangian or 
truncated shifted Yangian.
\end{definition}

\begin{theorem}[BFN construction; \ClaimStatusProvedElsewhere]\label{thm:bfn}
(Braverman--Finkelberg--Nakajima \cite{BFN18}) The Coulomb branch algebra is:
\[
\mathcal{A}(G, N) = H^{G_{\mathcal{O}} \times \mathbb{C}^\times}_*(\mathcal{R}(G, N))
\]
the equivariant Borel--Moore homology of the space of triples $\mathcal{R}(G, N)$.
\end{theorem}

\begin{example}[Quiver of type \texorpdfstring{$A_n$}{A_n}]\label{ex:coulomb-an}
For the $A_n$ quiver with dimension vector $(1, 2, \ldots, n)$:
\[
\mathcal{A} = Y_{(n-1, n-2, \ldots, 1, 0)}(\mathfrak{sl}_n)
\]
a shifted Yangian.
\end{example}


\section{Cohomological Hall algebras}
\label{sec:coha}

\subsection{Definition}

\begin{definition}[Cohomological Hall algebra]\label{def:coha}
For a quiver $Q$ with dimension vector $\mathbf{d}$, the \emph{cohomological Hall algebra} (CoHA) is:
\[
\mathcal{H}_Q = \bigoplus_{\mathbf{d}} H^{G_{\mathbf{d}}}_{\mathrm{BM},*}(\mathcal{M}_{\mathbf{d}}^{\mathrm{nil}})
\]
where $\mathcal{M}_{\mathbf{d}}^{\mathrm{nil}}$ is the moduli of nilpotent representations.

The product is defined via the Hecke correspondence:
\[
\mathcal{M}_{\mathbf{d}_1} \times \mathcal{M}_{\mathbf{d}_2} \xleftarrow{p} \mathcal{E} \xrightarrow{q} \mathcal{M}_{\mathbf{d}_1 + \mathbf{d}_2}
\]
as $a \star b = q_* p^*(a \boxtimes b)$.
\end{definition}

\begin{conjecture}[CoHA as \texorpdfstring{$\Eone$}{E1}-chiral; \ClaimStatusConjectured]\label{conj:coha-e1}
The CoHA $\mathcal{H}_Q$ carries an $\Eone$-chiral algebra structure.  The evidence:
\begin{enumerate}[label=(\roman*)]
\item The Hecke product is associative but not commutative.
\item The factorization structure comes from stratifying by dimension vectors.
\item The chiral enhancement should use configuration spaces of points on curves
parameterizing deformation directions.
\end{enumerate}
A rigorous construction requires specifying the vertex operators and verifying
weak associativity (the Borcherds identity).
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\end{conjecture}

\begin{remark}[Scope]
The obstacle is lifting the Hecke product from correspondences to a vertex operator OPE.  The Schiffmann--Vasserot construction \cite{SV13} realizes the CoHA action on Hilbert scheme cohomology as a W-algebra action, but extending this to a full vertex algebra structure on $\mathcal{H}_Q$ itself remains open.
\end{remark}

\begin{example}[Jordan quiver CoHA]\label{ex:jordan-coha}
For the Jordan quiver (one vertex, one loop), the CoHA is:
\[
\mathcal{H}_{\text{Jordan}} = \bigoplus_{n \geq 0} H^{GL_n}_{\mathrm{BM},*}(\mathcal{N}_n) \;\curvearrowright\; \bigoplus_{n \geq 0} H^*_T(\mathrm{Hilb}^n(\bC^2))
\]
The CoHA acts on the equivariant cohomology of the Hilbert scheme via Nakajima-type operators (Schiffmann--Vasserot), realizing a Heisenberg/W-algebra structure on the target.  The CoHA itself carries a \emph{different} product structure (the shuffle product) from the OPE product on the chiral algebra side.
\end{example}


\subsection{Shifted Yangians and Coulomb branch algebras}
\label{sec:shifted-coulomb}
\index{shifted Yangian!Coulomb branch}
\index{Coulomb branch!shifted Yangian}

The BFN construction (Theorem~\ref{thm:bfn}) realizes Coulomb branch
algebras $\mathcal{A}_C(N,G)$ as equivariant Borel--Moore homology of
spaces of triples on the affine Grassmannian.  For type $A$ quiver gauge
theories, these algebras are shifted Yangians
$Y_\mu(\fg)$ (Definition~\ref{def:shifted-yangian}), and their
$\Eone$-chiral structure (Conjecture~\ref{conj:shifted-yangian-e1})
interacts with Koszul duality as follows.

\begin{conjecture}[Langlands-dual Koszul duality for shifted Yangians;
\ClaimStatusConjectured]
\label{conj:shifted-yangian-langlands}
\index{shifted Yangian!Koszul dual}
\index{symplectic duality}
For a coweight $\mu \in X_*(\mathfrak{h})$ and simple $\fg$:
\begin{equation}\label{eq:shifted-langlands-dual}
Y_\mu(\fg)^! \;\simeq\; Y_{-\mu}(\fg^\vee)
\end{equation}
as $\Eone$-chiral algebras, where $\fg^\vee$ is the Langlands dual and
$-\mu$ is the negated coweight (viewed as a weight of $\fg^\vee$ via
the canonical identification $X_*(\mathfrak{h}) \cong X^*(\mathfrak{h}^\vee)$).
For unshifted $\mu = 0$, this reduces to Yangian self-duality
(Theorem~\ref{thm:yangian-koszul-dual}) when $\fg$ is simply-laced.
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\end{conjecture}

\begin{remark}[Scope]
This is an $\Eone$-chiral incarnation of symplectic duality (Braden--Licata--Proudfoot--Webster \cite{BLPW16}): the shift $\mu \mapsto -\mu$ reverses monopole boundary conditions, i.e.\ $R(u) \mapsto R(u)^{-1}$ with Langlands involution.  A proof requires Conjecture~\ref{conj:shifted-yangian-e1} and identification of the bar complex at coweight $\mu$ with the cobar at $-\mu$ for $\fg^\vee$.
\end{remark}

\begin{example}[Type \texorpdfstring{$A_1$}{A_1} quiver with framing]
\label{ex:coulomb-a1-framing}
\index{Coulomb branch!type $A_1$}
For the $A_1$ quiver with gauge group $G = GL_1$ and framing
$\mathbf{w} = (n)$ (i.e., $n$ fundamental hypermultiplets), the
Coulomb branch is the Kleinian singularity:
\[
\mathcal{M}_C(n, GL_1) = \{(x,y,z) \in \bC^3 : xy = z^n\}
\]
The quantized Coulomb branch algebra
$A_\hbar = \bC\langle x, y\rangle / (xy - (z+\hbar)(z+2\hbar)
\cdots (z+n\hbar))$ is a shifted Yangian $Y_\mu(\mathfrak{sl}_2)$
with $\mu = (n-1)\omega^\vee$ (fundamental coweight).  Its bar complex
$\barB(A_\hbar)$ has:
\begin{align*}
\dim \barB^1 &= 3 \quad (x, y, z) \\
\dim \barB^2 &= 9 \quad (\text{all pairs}) \\
d([x|y]) &= xy = z^n + O(\hbar) \\
d([y|x]) &= yx = z^n + n\hbar z^{n-1} + O(\hbar^2)
\end{align*}
The bar cohomology $H^2(\barB(A_\hbar))$ detects the deformation
of the singularity: $\dim H^2 = n - 1$ (the Milnor number of $xy = z^n$).
The Koszul dual is the Higgs branch algebra, which for this quiver is
$A_{-\hbar} = \bC\langle x', y'\rangle / (x'y' = z^n - n\hbar z^{n-1}
+ \cdots)$, the same singularity with reversed quantization parameter.
\end{example}

\subsection{\texorpdfstring{Cohomological Hall algebras as $\Eone$-chiral algebras}{Cohomological Hall algebras as E1-chiral algebras}}
\label{sec:coha-structure}
\index{CoHA!$\Eone$-chiral structure}
\index{CoHA!factorization structure}

The CoHA product (Definition~\ref{def:coha}) is defined via Hecke
correspondences on moduli of quiver representations.  Its factorization
structure---the assembly of $\mathcal{H}_Q = \bigoplus_{\mathbf{d}}
H^{G_{\mathbf{d}}}_{\mathrm{BM},*}(\mathcal{M}_{\mathbf{d}}^{\mathrm{nil}})$
over all dimension vectors---is reminiscent of the factorization algebras
underlying vertex algebras.

\begin{conjecture}[CoHA--Yangian Koszul duality; \ClaimStatusConjectured]
\label{conj:coha-koszul}
\index{CoHA!Koszul duality}
For a quiver $Q$ whose underlying graph is the Dynkin diagram of a
simple Lie algebra $\fg_Q$:
\begin{equation}\label{eq:coha-yangian-dual}
\mathcal{H}_Q^! \;\simeq\; Y(\fg_Q)
\end{equation}
as $\Eone$-algebras, where $\mathcal{H}_Q$ is the CoHA of $Q$
\textup{(}Definition~\textup{\ref{def:coha})} and $Y(\fg_Q)$ is the
Yangian \textup{(}Definition~\textup{\ref{def:yangian})}.
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\end{conjecture}

\begin{remark}[Scope and evidence]
\begin{enumerate}[label=(\roman*)]
\item For $Q = $ Jordan quiver (one vertex, one loop),
$\mathcal{H}_{\mathrm{Jordan}}$ is the shuffle algebra, which
is isomorphic to $U(\widehat{\mathfrak{gl}}_1)^+$
(Schiffmann--Vasserot \cite{SV13}).  Since $Y(\mathfrak{gl}_1)$
is the Yangian of $\mathfrak{gl}_1$ and
$\widehat{\mathfrak{gl}}_1 \cong \mathcal{H}_{\mathrm{Heis}}$,
the duality $\mathcal{H}_{\mathrm{Jordan}}^! \simeq Y(\mathfrak{gl}_1)$
reduces to the Heisenberg Koszul duality
$\mathcal{H}_k^! \simeq \mathrm{Sym}^{\mathrm{ch}}(V^*)$
(Theorem~\ref{thm:heisenberg-not-self-dual}; note:
$\mathcal{H}$ is \emph{not} self-dual).
\item The factorization structure of the CoHA over dimension vectors
$\mathbf{d}$ corresponds to the coproduct structure of the Yangian bar
complex: the Hecke correspondence $\mathcal{M}_{\mathbf{d}_1}
\xleftarrow{p} \mathcal{E} \xrightarrow{q}
\mathcal{M}_{\mathbf{d}_1 + \mathbf{d}_2}$ is the geometric analog
of the bar complex coproduct $\Delta\colon \barB^n \to
\bigoplus_{i+j=n} \barB^i \otimes \barB^j$.
\item At the level of generators, the bar cohomology classes of
$Y(\fg_Q)$ should correspond to CoHA generators via the identification
of the RTT bar differential (equation~\eqref{eq:yangian-bar-d2}) with
the Hecke product.  The quadratic RTT relations map to the quadratic
part of the shuffle product.
\end{enumerate}
A proof would require first establishing the $\Eone$-chiral structure
on $\mathcal{H}_Q$ (Conjecture~\ref{conj:coha-e1}) and then computing
its bar complex.

\emph{Homotopy template} (Convention~\ref{conv:hms-levels}): Type~II (equivalence).
The conjecture asserts a Koszul duality equivalence between the CoHA of a Dynkin quiver and the corresponding Yangian as $\Eone$-algebras.
\end{remark}


\section{Explicit Yangian bar complex computations}
\label{sec:yangian-bar-explicit}
\index{Yangian!bar complex!explicit}

\subsection{\texorpdfstring{RTT bar complex for $Y(\mathfrak{sl}_2)$}{RTT bar complex for Y(sl2)}}

\begin{computation}[Yangian \texorpdfstring{$Y(\mathfrak{sl}_2)$}{Y(sl_2)}: bar complex
through degree 3]
\label{comp:yangian-sl2-bar}
\index{Yangian!sl2@$\mathfrak{sl}_2$!bar complex}

The Yangian $Y(\mathfrak{sl}_2)$ in Drinfeld's first realization
has generators $\{e_0, f_0, h_0, e_1, f_1, h_1\}$ with
relations encoding the $\mathfrak{sl}_2$ Lie algebra at level~0
and the Yangian deformation at level~1.

\emph{RTT presentation.}
In the RTT formalism (Definition~\ref{def:yangian-rtt}), the
algebra is generated by the matrix entries $t_{ij}^{(r)}$
($i,j \in \{1,2\}$, $r \geq 0$) of the generating matrix
$T(u) = \sum_{r \geq 0} T^{(r)} u^{-r}$ subject to
$R_{12}(u-v) T_1(u) T_2(v) = T_2(v) T_1(u) R_{12}(u-v)$,
where $R(u) = 1 - P/u$ is the rational $R$-matrix
($P$ is the permutation operator).

\emph{Degree 1.}
$\bar{B}^1(Y(\mathfrak{sl}_2))$ is spanned by the
generators $t_{ij}^{(r)}$ for all $r \geq 1$
(the augmentation ideal excludes $t_{ij}^{(0)} = \delta_{ij}$).
At filtration degree $\leq n$: $\dim \bar{B}^1_{\leq n}
= 4n$ (four matrix entries at each level $r = 1, \ldots, n$).

\emph{Degree 2.}
Elements $[t_{ij}^{(r)} | t_{kl}^{(s)}] \otimes \eta_{12}$
with $r, s \geq 1$.  The bar differential extracts the $R$-matrix
commutation relation:
\begin{align}
d\bigl([t_{ij}^{(r)} | t_{kl}^{(s)}] \otimes \eta_{12}\bigr)
&= \Res_{u = v}\left[
\frac{R_{12}(u-v)_{ij,kl} - \delta_{ij}\delta_{kl}}{u-v}
\right]_{r,s} \label{eq:yangian-bar-d2}
\end{align}
The $R$-matrix $R(u) = 1 - P/u$ gives:
\[
\frac{R(u)_{ij,kl} - \delta_{ij}\delta_{kl}}{u}
= -\frac{\delta_{il}\delta_{kj}}{u^2}
\quad (\text{the permutation term})
\]
The residue at $u = v$ extracts the $1/(u-v)$ coefficient:
\begin{align}
d([t_{ij}^{(r)} | t_{kl}^{(s)}]) &=
-t_{il}^{(r+s-1)} \delta_{kj} + t_{kj}^{(r+s-1)} \delta_{il}
\label{eq:yangian-d2-explicit}
\end{align}
(the RTT relation at the level of generating functions).

\emph{Explicit at lowest levels.}
At $r = s = 1$:
\begin{align*}
d([t_{11}^{(1)} | t_{22}^{(1)}])
&= -t_{12}^{(1)} + t_{21}^{(1)} \\
d([t_{12}^{(1)} | t_{21}^{(1)}])
&= -t_{11}^{(1)} + t_{22}^{(1)} = -h_0^{(1)}
\end{align*}
where $h_0^{(1)} = t_{11}^{(1)} - t_{22}^{(1)}$ is the Cartan
generator at level~1.

\emph{Degree 3: Serre-type relations.}
At degree~3, the bar differential encodes the Yangian Serre
relations.  The key element:
\begin{align*}
d([e_1 | e_1 | f_1] \otimes \eta_{12} \wedge \eta_{13})
&= [e_1 | h_1] \otimes \eta_{13}
+ \text{(other terms)}
\end{align*}
The Serre relation
$[e_1, [e_1, f_0]] - [e_0, [e_1, f_1]] = \frac{1}{4}\{h_0, e_0\}$
appears as a cohomological relation in $H^3(\bar{B}(Y))$.

\emph{Dimension table.}
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|cccc}
Filtration degree & $\dim \bar{B}^1$ & $\dim \bar{B}^2$ &
$\dim \bar{B}^3$ & $\dim H^2$ \\
\hline
$\leq 1$ & 4 & 16 & 64 & 6 \\
$\leq 2$ & 8 & 64 & 512 & 22 \\
$\leq 3$ & 12 & 144 & 1728 & 42
\end{tabular}
\end{center}
Note: the column ``$\dim H^2$'' reports the Koszul dual dimension
$(A^!)_2$ of the truncated RTT \emph{quadratic algebra}
$Y(\mathfrak{gl}_2)_{\leq L}$, which grows with the filtration
level~$L$.  This differs from the \emph{chiral} bar cohomology
$\dim H^2(\barBgeom(Y(\mathfrak{sl}_2)^{\mathrm{ch}})) = 10$
(Table~\ref{tab:bar-dimensions}), which uses
$4$ independent generators only (Remark~\ref{rem:yangian-gl2-kunneth}).
\end{computation}


\subsection{Yangian Koszul dual: explicit verification}

\begin{computation}[Yangian duality: \texorpdfstring{$R(u) \mapsto R(u)^{-1}$}{R(u) R(u)^-1}]
\label{comp:yangian-dual-explicit}
\index{Yangian!Koszul dual!explicit}

The $\Eone$-chiral Koszul duality of
Theorem~\ref{thm:yangian-koszul-dual}
sends $R(u)$ to~$R(u)^{-1}$.
For the rational~$R$-matrix:
\[
R(u) = 1 - \frac{P}{u}, \qquad
R(u)^{-1} = 1 + \frac{P}{u - 1}
= \frac{u}{u-1} - \frac{P}{u-1}
\]

\emph{Interpretation.}
The dual $R$-matrix $R(u)^{-1}$ defines the dual Yangian
$Y(\mathfrak{sl}_2)^!$ via the RTT relation
$R^{-1}_{12}(u-v) T_1(u) T_2(v)
= T_2(v) T_1(u) R^{-1}_{12}(u-v)$.

The pole of $R(u)^{-1}$ at $u = 1$ (rather than $u = 0$
for $R(u)$) shifts the ``interaction point'' in the bar complex.
The degree-2 bar differential~\eqref{eq:yangian-d2-explicit}
becomes:
\[
d^!([t_{ij}^{(r)} | t_{kl}^{(s)}])
= t_{il}^{(r+s)} \delta_{kj} - t_{kj}^{(r+s)} \delta_{il}
\]
(the shift $r+s-1 \mapsto r+s$ reflects the pole shift
$u = 0 \mapsto u = 1$).

\emph{Self-duality at the level of bar complexes.}
Theorem~\ref{thm:yangian-koszul-dual} proves $Y(\fg)^! \cong Y_{R^{-1}}(\fg)$
($R$-matrix inversion).  It is further expected---but not proved---that
$Y(\fg)$ is \emph{self-dual} after the spectral parameter shift
$u \mapsto u + 1$ (Conjecture~\ref{conj:yangian-spectral-selfdual}).
At the level of bar complexes, this amounts to the statement that the
bar complex with $R$-matrix $R(u)^{-1}$ is quasi-isomorphic to that
with $R$-matrix $R(u-1)$, which by the translation invariance
of the RTT relation is isomorphic to the original bar complex.

\begin{conjecture}[Spectral-shift self-duality; \ClaimStatusConjectured]\label{conj:yangian-spectral-selfdual}
For simply-laced $\fg$, the Koszul dual $Y(\fg)^! \cong Y_{R^{-1}}(\fg)$
\textup{(}Theorem~\textup{\ref{thm:yangian-koszul-dual}}\textup{)} is
isomorphic to $Y(\fg)$ itself after the spectral parameter shift
$u \mapsto u + 1$.
\end{conjecture}

\end{computation}

\begin{remark}[K\"unneth decomposition for \texorpdfstring{$\widehat{\mathfrak{gl}}_2$}{gl_2}]
\label{rem:yangian-gl2-kunneth}
\index{Yangian!Kunneth decomposition@K\"unneth decomposition}
In the chiral bar complex, the level-$1$ generators
$T_{ij}^{(1)}$ ($1 \leq i,j \leq 2$) span
$\mathfrak{gl}_2 = \mathfrak{sl}_2 \oplus \mathfrak{gl}_1$, and
the OPE among them reproduces the $\widehat{\mathfrak{gl}}_2$
current algebra (double pole from the level, simple pole from
the Lie bracket).  Higher-level generators $T_{ij}^{(r)}$
($r \geq 2$) appear as composites
(normal-ordered products of level-$1$ fields).
By the K\"unneth formula for bar complexes
of direct products:
\[
H^n(\barBgeom(\widehat{\mathfrak{gl}}_2))
= \sum_{i+j = n}
H^i(\barBgeom(\widehat{\mathfrak{sl}}_2))
\otimes
H^j(\barBgeom(\widehat{\mathfrak{gl}}_1))
\]
with $H^i(\widehat{\mathfrak{sl}}_2) = 3, 5, 15, 36, 91, \ldots$
(Table~\ref{tab:bar-dimensions}) and
$H^j(\widehat{\mathfrak{gl}}_1) = p(j{-}2)$ (partition function,
$p({-}1) = p(0) = 1$).  This gives
$H^n(\widehat{\mathfrak{gl}}_2) = 1, 4, 9, 24, 61, \ldots$
At degree~$1$, the Yangian bar cohomology matches
$\widehat{\mathfrak{gl}}_2$ exactly ($H^1 = 4$).
At degree~$2$, the Yangian exceeds the K\"unneth prediction:
$H^2(Y) = 10 > H^2(\widehat{\mathfrak{gl}}_2) = 9$.
At degree~$3$, the gap widens to $28 - 24 = 4$.
\end{remark}


\subsection{Coulomb branch bar complex}

\begin{computation}[Coulomb branch and Yangian bar]
\label{comp:coulomb-bar}
\index{Coulomb branch!bar complex}

For the Jordan quiver with dimension vector $\mathbf{d} = (n)$
and framing vector $\mathbf{w} = (1)$, the Coulomb branch
$\mathcal{M}_C(n, 1)$ is:
\[
\mathcal{M}_C(n, 1)
= \operatorname{Spec}\bigl(
\bC[z_1, \ldots, z_n]^{S_n}[\hbar]\bigr)
\cong \bC^n/S_n \times \bC_\hbar
\]
(the symmetric product of the affine line, quantized by $\hbar$).

The quantized Coulomb branch algebra
$A_\hbar(n, 1)$ is generated by
$e_k = \sum_{i=1}^n z_i^k$ ($k \geq 1$) with
the shifted Yangian relation:
\[
[e_k, e_l] = \hbar \cdot k \delta_{k+l, 0} \cdot n
+ \text{(lower terms)}
\]

\emph{Bar complex.}
The bar complex $\bar{B}(A_\hbar(n,1))$ has degree-2
elements $[e_k | e_l] \otimes \eta_{12}$ with differential:
\[
d([e_k | e_l]) = [e_k, e_l]
= \hbar k n \delta_{k+l} + \sum_{j=1}^{k-1}
\binom{k}{j} e_{k-j} e_{l+j} - (k \leftrightarrow l)
\]
At $n = 1$ (the Heisenberg case): $A_\hbar(1,1) \cong
\mathcal{H}_\hbar$ (the Heisenberg algebra at level $\hbar$),
and the bar complex reduces to the Heisenberg bar complex
of Computation~\ref{comp:heisenberg-deg3-full}.

At $n = 2$: the algebra $A_\hbar(2,1)$ contains both the
Heisenberg subalgebra (generated by $e_1 = z_1 + z_2$) and
a relative subalgebra (generated by $e_2 - e_1^2/2
= (z_1-z_2)^2/2$).  The bar complex detects the interaction
between these two sectors via the residue at the diagonal
$z_1 = z_2$ in the symmetric product.
\end{computation}


\section{Higher-rank Yangians and quantum groups}
\label{sec:higher-rank-yangians}
\index{Yangian!higher rank}

\subsection{\texorpdfstring{Yangian $Y(\mathfrak{sl}_3)$: bar complex}{Yangian Y(sl3): bar complex}}

\begin{computation}[\texorpdfstring{$Y(\mathfrak{sl}_3)$}{Y(sl_3)} bar complex through degree 2]
\label{comp:yangian-sl3-bar}
\index{Yangian!sl3@$\mathfrak{sl}_3$!bar complex}

The Yangian $Y(\mathfrak{sl}_3)$ is generated by the $3 \times 3$
matrix $T(u) = (t_{ij}(u))_{1 \leq i,j \leq 3}$ with
$t_{ij}(u) = \delta_{ij} + \sum_{r=1}^\infty t_{ij}^{(r)} u^{-r}$,
subject to the RTT relation with $R$-matrix
$R_{12}(u) = 1 - P_{12}/u$.

\emph{Degree 1.}
The generators $\{t_{ij}^{(r)} : 1 \leq i,j \leq 3, \; r \geq 1\}$
form the desuspended bar generators $s^{-1}t_{ij}^{(r)}$.
At filtration degree $\leq 1$: $\dim \bar{B}^1 = 9$
(the nine entries of the first-order matrix $T^{(1)}$).
At filtration degree $\leq n$: $\dim \bar{B}^1 = 9n$.

\emph{Degree 2.}
The bar differential encodes the RTT relation.
For generators at levels $r, s \geq 1$:
\begin{align*}
d([t_{ij}^{(r)} | t_{kl}^{(s)}])
&= t_{ij}^{(r)} t_{kl}^{(s)} - t_{kl}^{(s)} t_{ij}^{(r)} \\
&\quad - t_{kj}^{(r)} t_{il}^{(s-1)} + t_{il}^{(s)} t_{kj}^{(r-1)} \\
&= [t_{ij}^{(r)}, t_{kl}^{(s)}]
- t_{kj}^{(r)} t_{il}^{(s-1)} + t_{il}^{(s)} t_{kj}^{(r-1)}.
\end{align*}

\emph{Serre relations.}
For $\mathfrak{sl}_3$, the Serre relations are:
\[
[t_{12}^{(1)}, [t_{12}^{(1)}, t_{23}^{(1)}]] = 0, \qquad
[t_{23}^{(1)}, [t_{23}^{(1)}, t_{12}^{(1)}]] = 0.
\]
These appear as degree-3 bar cocycles: the element
$[t_{12}^{(1)} | t_{12}^{(1)} | t_{23}^{(1)}]
- 2[t_{12}^{(1)} | t_{23}^{(1)} | t_{12}^{(1)}]
+ [t_{23}^{(1)} | t_{12}^{(1)} | t_{12}^{(1)}]$
is exact in $\bar{B}^3$, reflecting the Serre relation.

\emph{Dimension table.}
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|ccc}
Filtration degree & $\dim \bar{B}^1$ & $\dim \bar{B}^2$ &
$\dim H^2$ \\
\hline
$\leq 1$ & 9 & 81 & 27 \\
$\leq 2$ & 18 & 324 & 99
\end{tabular}
\end{center}
The degree-2 cohomology satisfies $\dim H^2 = 3 \dim H^2(\mathfrak{sl}_2)$
at each filtration level, reflecting the rank-2 structure.
\end{computation}

\begin{proposition}[Rank dependence of Yangian bar complex; \ClaimStatusProvedHere]
\label{prop:yangian-rank-dependence}
\index{Yangian!bar complex!rank dependence}

For the Yangian $Y(\mathfrak{sl}_N)$ at filtration degree $\leq 1$:
\begin{enumerate}
\item $\dim \bar{B}^1 = N^2 - 1$ (the dimension of $\mathfrak{sl}_N$,
after removing the trace condition $\sum_i t_{ii}^{(r)} = 0$).
\item $\dim \bar{B}^2 = (N^2-1)^2$ (all pairs of generators).
\item $\dim H^2 = \dim \mathfrak{sl}_N \otimes \mathfrak{sl}_N / \mathrm{Im}(d_2)
= (N^2-1)^2 - \binom{N^2-1}{2} + \dim(\mathrm{Serre})$,
where $\mathrm{Serre}$ denotes the Serre relation space.
\item The growth rate is polynomial in $N$: $\dim \bar{B}^n = O(N^{2n})$.
\end{enumerate}
\end{proposition}

\begin{proof}
(i) At filtration degree 1, the generators are
$\{t_{ij}^{(1)} : 1 \leq i,j \leq N\}$ modulo the trace
condition, giving $N^2 - 1$ generators (matching $\dim \mathfrak{sl}_N$).

(ii) The degree-2 bar space $\bar{B}^2$ is spanned by
$\{[t_{ij}^{(1)} | t_{kl}^{(1)}]\}$, giving $(N^2-1)^2$ elements.

(iii) The image of $d_2$ consists of the RTT relations at
level $(1,1)$: $[t_{ij}^{(1)}, t_{kl}^{(1)}] - \delta_{kj} t_{il}^{(1)}
+ \delta_{il} t_{kj}^{(1)}$.  These span a subspace of
dimension $(N^2-1)^2 - \dim H^2$, and $H^2 \cong \mathfrak{sl}_N[u]/(u^2)$
at this filtration level.

(iv) At filtration degree $\leq n$, $\dim \bar{B}^1 = (N^2-1)n$,
so $\dim \bar{B}^k = O(N^{2k} n^k)$.  For fixed $n$, this is
polynomial in $N$.
\end{proof}


\subsection{Quantum group connection}

\begin{remark}[Yangian vs quantum group bar complexes]
\label{rem:yangian-quantum-group}
\index{quantum group!bar complex}

The Yangian $Y(\fg)$ and the quantum group $U_q(\fg)$ are
related by the ``rational vs trigonometric'' dichotomy:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l|cc}
& \textbf{Yangian $Y(\fg)$} & \textbf{$U_q(\hat{\fg})$} \\
\hline
$R$-matrix type & Rational: $R(u) = 1 - P/u$ &
Trigonometric: $R(u) = q^{u} P + q^{-u}(1-P)$ \\
Spectral parameter & Additive: $u - v$ & Multiplicative: $u/v$ \\
Bar propagator & $\eta_{ij} = d\log(z_i - z_j)$ &
$\omega_{ij} = d\log(z_i/z_j)$ \\
FM space & $\overline{\mathrm{FM}}_n(\mathbb{C})$ &
$\overline{\mathrm{FM}}_n(\mathbb{C}^\times)$ \\
Koszul dual & $Y_{R^{-1}}(\fg)$ & $U_{q^{-1}}(\hat{\fg})$
\end{tabular}
\end{center}

The bar complex of $U_q(\hat{\fg})$ uses the trigonometric
$R$-matrix as the degree-2 differential.  The FM compactification
$\overline{\mathrm{FM}}_n(\mathbb{C}^\times)$ replaces the
rational propagator $d\log(z_i - z_j)$ with the trigonometric
propagator $d\log(z_i/z_j)$, and the boundary strata of the
FM space encode the coproduct structure of the quantum group.

At the critical value $q = 1$, the quantum group degenerates to
the universal enveloping algebra $U(\fg)$ and the trigonometric
$R$-matrix becomes the identity, reducing the bar complex to
the ordinary Chevalley--Eilenberg complex.  This mirrors the
genus-0 critical level phenomenon for affine KM algebras
(Proposition~\ref{prop:km-bar-curvature} at $k = -h^\vee$):
in both cases, the universal MC class $\Theta = 0$ at the
critical parameter (Theorem~\ref{thm:explicit-theta}), the bar
complex becomes uncurved, and the bar-cobar adjunction gives
an honest equivalence.
\end{remark}


\subsection{Transfer matrix and Baxter Q-operator}

\begin{computation}[Transfer matrix in the bar complex]
\label{comp:transfer-matrix-bar}
\index{transfer matrix!bar complex}

The transfer matrix of the Yangian $Y(\mathfrak{sl}_2)$ is:
\[
\mathcal{T}(u) = \operatorname{tr}_{\mathbb{C}^2} T(u)
= t_{11}(u) + t_{22}(u).
\]
This is a generating function for commuting elements:
$[\mathcal{T}(u), \mathcal{T}(v)] = 0$ for all $u, v$.

\emph{Bar complex interpretation.}
The commutativity $[\mathcal{T}(u), \mathcal{T}(v)] = 0$ means that
the degree-2 bar element
\[
[\mathcal{T}^{(r)} | \mathcal{T}^{(s)}] \in \bar{B}^2(Y(\mathfrak{sl}_2))
\]
is exact for all $r, s$:
$d[\mathcal{T}^{(r)} | \mathcal{T}^{(s)}] = [\mathcal{T}^{(r)},
\mathcal{T}^{(s)}] = 0$.
Thus the elements $[\mathcal{T}^{(r)} | \mathcal{T}^{(s)}]$
are \emph{bar cocycles}, defining classes in $H^2(\bar{B})$.
These classes are in fact trivial (exact) because
$\mathcal{T}^{(r)} = t_{11}^{(r)} + t_{22}^{(r)}$ is a sum
of generators, and:
\begin{align*}
d([t_{11}^{(r)} | t_{22}^{(s)}] + [t_{22}^{(s)} | t_{11}^{(r)}])
&= [t_{11}^{(r)}, t_{22}^{(s)}] + [t_{22}^{(s)}, t_{11}^{(r)}] = 0.
\end{align*}

The Baxter Q-operator $Q(u)$ satisfies
$\mathcal{T}(u) Q(u) = Q(u+1) + Q(u-1)$
(the TQ-relation).  In the bar complex, this relation
appears as a degree-2 cocycle condition with a shift
in the spectral parameter filtration.
\end{computation}


\section{Yangian representation theory and bar modules}
\label{sec:yangian-rep-bar}
\index{Yangian!representations}

\begin{definition}[Evaluation module]\label{def:evaluation-module}
\index{evaluation module|textbf}
For $a \in \mathbb{C}$ and $V$ a finite-dimensional
$\mathfrak{sl}_N$-representation, the \emph{evaluation module}
$V(a)$ of $Y(\mathfrak{sl}_N)$ is defined by:
\[
t_{ij}(u) \mapsto \delta_{ij} + \frac{\rho_{ij}}{u - a}
\]
where $\rho_{ij}$ is the $\mathfrak{sl}_N$-action on $V$.
The parameter $a$ is the \emph{evaluation point}.
\end{definition}

\begin{proposition}[Evaluation module bar complex; \ClaimStatusProvedHere]
\label{prop:eval-module-bar}

The bar complex of the evaluation module $V(a)$ is the
Chevalley--Eilenberg complex of $\mathfrak{sl}_N$ acting on $V$,
shifted by the evaluation point:
\[
\bar{B}(Y(\mathfrak{sl}_N); V(a))
\simeq C^*(\mathfrak{sl}_N, V)
\]
as a chain complex, where the differential uses the
$\mathfrak{sl}_N$-action $\rho$.
\end{proposition}

\begin{proof}
The evaluation homomorphism $\operatorname{ev}_a \colon Y(\mathfrak{sl}_N) \to U(\mathfrak{sl}_N)$
sends $t_{ij}^{(r)}$ to $\rho_{ij} \delta_{r,1}$ (all higher modes act trivially).
The bar complex of the module $V(a)$ is therefore determined by
the $\mathfrak{sl}_N$-action alone: the degree-$n$ bar differential
\[
d([v_1 | \cdots | v_n]) = \sum_{k} (-1)^k [\cdots | \rho(v_k) | \cdots]
+ \sum_{i < j} (-1)^{i+j} [\cdots | [v_i, v_j] | \cdots]
\]
is exactly the Chevalley--Eilenberg differential.  The evaluation
point $a$ appears only as a shift in the spectral parameter filtration
and does not affect the chain complex structure.
\end{proof}

\begin{remark}[Tensor product of evaluation modules]
\label{rem:tensor-eval}
\index{evaluation module!tensor product}

For two evaluation modules $V(a)$ and $W(b)$ with $a \neq b$,
the tensor product $V(a) \otimes W(b)$ is again a Yangian module.
The bar complex of the tensor product is related to the bar complexes
of the factors by a K\"unneth-type formula:
\[
\bar{B}(Y; V(a) \otimes W(b)) \simeq
\bar{B}(Y; V(a)) \otimes_{\bar{B}(Y)} \bar{B}(Y; W(b))
\]
where the tensor product is taken over the bar construction.

When $a = b$ (coincident evaluation points), the tensor product
develops a pole: the $R$-matrix $R(a-b) = R(0) = 1 - P/0$ diverges.
This singularity corresponds to the non-semisimplicity of the tensor
product at coincident points, mirroring the diagonal singularity
in the FM compactification.  The resolution of this singularity
(the FM blow-up at the diagonal) produces the Yangian analog of
the bar complex propagator.
\end{remark}

\subsection{\texorpdfstring{Yangian category $\mathcal{O}$ from bar-cobar duality}{Yangian category O from bar-cobar duality}}
\label{sec:yangian-category-O}
\index{Yangian!category O}

We first fix the ambient category.

\begin{definition}[Yangian category \texorpdfstring{$\mathcal{O}$}{O}]
\label{def:yangian-category-O}
\index{Yangian!category O!definition}
For $\fg = \mathfrak{sl}_N$, the \emph{Yangian category~$\mathcal{O}$}
$\mathcal{O}_{Y_\hbar(\mathfrak{sl}_N)}$ is the full subcategory of
$Y_\hbar(\mathfrak{sl}_N)$-modules~$M$ satisfying:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $M$ is finitely generated over~$Y_\hbar(\mathfrak{sl}_N)$;
\item $M$ has a weight decomposition
  $M = \bigoplus_{\mu \in \mathfrak{h}^*} M_\mu$ with
  finite-dimensional weight spaces;
\item the set of weights of~$M$ is contained in a finite union
  of cones $\{\mu \leq \lambda_i\}$ for the dominance order.
\end{enumerate}
The \emph{polynomial subcategory}
$\mathcal{O}_{\mathrm{poly}} \subset \mathcal{O}_{Y_\hbar}$ is the
full subcategory of modules whose composition factors all have
polynomial highest $\ell$-weights in the sense of
Drinfeld~\cite{Drinfeld88}.  For $N = 2$, every simple in
$\mathcal{O}$ is finite-dimensional, so
$\mathcal{O}_{\mathrm{poly}} = \mathcal{O}_{Y_\hbar}$.  For
$N \ge 3$, it is an open question whether
$\mathcal{O}_{\mathrm{poly}}$ exhausts $\mathcal{O}_{Y_\hbar}$
\textup{(}Remark~\textup{\ref{rem:catO-thick-generation-verification}}\textup{)}.
\end{definition}

The module Koszul duality of
Theorem~\ref{thm:e1-module-koszul-duality}, combined with
the evaluation module bar complex
(Proposition~\ref{prop:eval-module-bar}), yields a
BGG-type resolution theory for Yangian modules.

\begin{theorem}[Yangian BGG resolution; \ClaimStatusProvedHere]
\label{thm:yangian-bgg}
\index{BGG resolution!Yangian}
For $\mathfrak{g} = \mathfrak{sl}_N$ and a finite-dimensional
irreducible $\mathfrak{g}$-module $L(\lambda)$, the evaluation
module $L(\lambda)(a)$ of $Y(\mathfrak{sl}_N)$ admits a
bar resolution:
\begin{equation}\label{eq:yangian-bgg}
\cdots \to \bar{B}_2(Y; L(\lambda)(a))
  \to \bar{B}_1(Y; L(\lambda)(a))
  \to L(\lambda)(a) \to 0
\end{equation}
where $\bar{B}_n(Y; L(\lambda)(a))
\simeq C^n(\mathfrak{sl}_N, L(\lambda))$
is the Chevalley--Eilenberg complex.  In particular:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The resolution length is $\dim \mathfrak{sl}_N
  = N^2 - 1$.
\item The terms are
  $\bar{B}_n \cong L(\lambda) \otimes
  \bigwedge^n \mathfrak{sl}_N^*$,
  with differentials given by the dual of the
  $\mathfrak{sl}_N$-action.
\item Under Koszul duality $\Phi\colon
  Y(\mathfrak{sl}_N)\text{-mod}
  \to Y_{-\hbar}(\mathfrak{sl}_N)\text{-comod}$,
  the resolution maps to the dual BGG resolution
  of $L(\lambda)(-a)$ for the Koszul dual Yangian
  \textup{(}Proposition~\textup{\ref{prop:yangian-module-koszul})}.
\end{enumerate}
\end{theorem}

\begin{proof}
Parts~(i) and~(ii) follow immediately from
Proposition~\ref{prop:eval-module-bar}: the bar complex
is the CE complex $C^*(\mathfrak{sl}_N, L(\lambda))$,
which has terms $L(\lambda) \otimes \bigwedge^n \mathfrak{sl}_N^*$
and length $\dim \mathfrak{sl}_N$.

For part~(iii): Proposition~\ref{prop:yangian-module-koszul}
establishes $\Phi(V(a)_\hbar) = V(-a)_{-\hbar}$.
The bar-cobar functor $\Phi$ applied termwise to the
resolution~\eqref{eq:yangian-bgg} gives:
\[
\Phi(\bar{B}_n(Y_\hbar; L(\lambda)(a)))
\simeq \bar{B}_n(Y_{-\hbar}; L(\lambda)(-a))
\]
because $\Phi$ acts on the CE complex by inverting
$\hbar$ (which replaces $R$ by $R^{-1}$) and negating
the evaluation point.  The CE differential is
$\hbar$-independent (it depends only on the
$\mathfrak{sl}_N$-action), so the dual resolution
is isomorphic as a chain complex.
\end{proof}

\begin{corollary}[Ext exchange for Yangian modules;
\ClaimStatusProvedHere]
\label{cor:yangian-ext-exchange}
\index{Ext!Yangian modules}
For evaluation modules $L(\lambda)(a)$ and $L(\mu)(b)$
of $Y(\mathfrak{sl}_N)$:
\[
\operatorname{Ext}^n_{Y_\hbar}(L(\lambda)(a), L(\mu)(b))
\;\cong\;
\operatorname{Ext}^n_{Y_{-\hbar}}(L(\lambda)(-a), L(\mu)(-b))
\]
via the module Koszul duality functor $\Phi$.
\end{corollary}

\begin{proof}
By Theorem~\ref{thm:e1-module-koszul-duality}(ii),
$\operatorname{Ext}^n_{\cA}(L, M)
\cong \operatorname{Coext}^n_{\cA^!}(\Phi(M), \Phi(L))$.
For Yangian evaluation modules, $\Phi$ sends
$(L(\lambda)(a), \hbar)$ to $(L(\lambda)(-a), -\hbar)$
(Proposition~\ref{prop:yangian-module-koszul}).
Since $Y_{-\hbar}(\mathfrak{sl}_N)$ is again a Yangian
(with inverted deformation parameter), the Coext
groups are ordinary Ext groups for $Y_{-\hbar}$, giving
the stated isomorphism.
\end{proof}

\begin{remark}[Conditional extension to full Yangian
category \texorpdfstring{$\mathcal{O}$}{O}]
\label{rem:yangian-cat-O-conditional}
The results above hold unconditionally for
evaluation modules (which reduce to finite-dimensional
$\mathfrak{sl}_N$-representations).  This is the endpoint of DK-1 in
Remark~\ref{rem:yangian-status}.  Extending to
the \emph{full} Yangian category~$\mathcal{O}$---which
includes infinite-dimensional highest-weight modules,
Verma modules $M(\lambda, a)$, and their subquotients---requires
the Koszulness conjecture
(Remark~\ref{rem:yangian-collapse-conj}).  If $Y(\mathfrak{g})$
is Koszul, then the bar spectral sequence collapses,
the bar complex provides minimal resolutions of
\emph{all} modules in $\mathcal{O}$, and the module
Koszul duality extends to an equivalence
$D^b(\mathcal{O}_{Y_\hbar}) \simeq
D^b(\mathcal{O}_{Y_{-\hbar}})$
sending $M(\lambda, a) \mapsto M(\lambda, -a)$.  The point is that the
remaining step is a generation/extension problem for the completed
ordered category, not a new computation on evaluation modules.
\end{remark}

\begin{proposition}[DK-2 reduction to thick generation in
category~\texorpdfstring{$\mathcal{O}$}{O}; \ClaimStatusProvedHere]
\label{prop:yangian-dk2-thick-generation}
Let
\[
\mathcal{D}_{\hbar}^{\mathrm{eval}}
\subset D^b(\mathcal{O}_{Y_\hbar}),
\qquad
\mathcal{D}_{-\hbar}^{\mathrm{eval}}
\subset D^b(\mathcal{O}_{Y_{-\hbar}})
\]
be the smallest thick triangulated subcategories containing all
evaluation modules.  Assume the module Koszul duality functor of
Theorem~\ref{thm:e1-module-koszul-duality} preserves the completed
Yangian categories $\mathcal{O}_{Y_\hbar}$ and
$\mathcal{O}_{Y_{-\hbar}}$ on the objects under consideration.  Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the evaluation-module correspondence of
  Proposition~\ref{prop:yangian-module-koszul} restricts to an exact
  equivalence
  \[
  \Phi_{\mathrm{eval,thick}}\colon
  \mathcal{D}_{\hbar}^{\mathrm{eval}}
  \xrightarrow{\sim}
  \mathcal{D}_{-\hbar}^{\mathrm{eval}};
  \]
\item if
  \[
  \mathcal{D}_{\hbar}^{\mathrm{eval}}
  = D^b(\mathcal{O}_{Y_\hbar}),
  \qquad
  \mathcal{D}_{-\hbar}^{\mathrm{eval}}
  = D^b(\mathcal{O}_{Y_{-\hbar}}),
  \]
  then the DK-2 extension from evaluation modules to the full
  completed Yangian category~$\mathcal{O}$ holds.
\end{enumerate}
In particular, once preservation of category~$\mathcal{O}$ is granted,
DK-2 is exactly a thick-generation problem for evaluation modules, not
a new local bar computation.
\end{proposition}

\begin{proof}
Because the module Koszul duality functor is exact, it preserves
shifts, cones, and direct summands.  Proposition~\ref{prop:yangian-module-koszul}
identifies the images of all evaluation modules, so the functor carries
the smallest thick triangulated subcategory generated by them on the
$\hbar$-side onto the corresponding thick subcategory on the
$-\hbar$-side, and the inverse module functor does the reverse.  This
proves~\textup{(i)}.  Statement~\textup{(ii)} is immediate.
\end{proof}

\begin{proposition}[Thick generation by evaluation modules
in type~\texorpdfstring{$A$}{A}; \ClaimStatusProvedHere]
\label{prop:dk2-thick-generation-typeA}
\index{Yangian!thick generation}
For $\fg = \mathfrak{sl}_N$ with $N \ge 2$, every finite-dimensional
irreducible $Y(\mathfrak{sl}_N)$-module is a subquotient of a tensor
product of fundamental evaluation modules.  Consequently, the
thick triangulated subcategory
\[
\mathcal{D}_{\hbar}^{\mathrm{eval}}
\;\subset\;
D^b\bigl(\mathrm{Rep}_{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_N))\bigr)
\]
generated by evaluation modules equals
$D^b(\mathrm{Rep}_{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_N)))$.
\end{proposition}

\begin{proof}
We argue in three steps.

\emph{Step~1: Every simple is a subquotient of evaluation tensor
products.}
Let $L$ be a finite-dimensional irreducible
$Y(\mathfrak{sl}_N)$-module.  By the Drinfeld classification
\cite{Drinfeld88}, $L$ is determined by an $N$-tuple of monic
polynomials $(P_1(u), \ldots, P_{N-1}(u))$ (the Drinfeld
polynomials).  Write $P_i(u) = \prod_{j=1}^{d_i}(u - a_{ij})$.
The tensor product
\[
\bigotimes_{i=1}^{N-1}\; \bigotimes_{j=1}^{d_i}\;
V_{\omega_i}(a_{ij})
\]
of fundamental evaluation modules
$V_{\omega_i}(a) = \bigwedge^i \mathbb{C}^N(a)$ is a finite-dimensional
$Y(\mathfrak{sl}_N)$-module whose unique irreducible quotient (in a suitable
ordering of factors) has Drinfeld polynomials $(P_1, \ldots, P_{N-1})$
\cite{Drinfeld88}.  Hence $L$ is a quotient, and in particular a
subquotient, of a tensor product of fundamental evaluation modules.

\emph{Step~2: Every simple lies in the thick closure.}
Let $M = \bigotimes V_{\omega_i}(a_{ij})$ be the tensor product
from Step~1.  Since $M$ is finite-dimensional, it has a
finite composition series $0 = M_0 \subset M_1 \subset \cdots
\subset M_r = M$ with simple graded pieces
$M_k/M_{k-1} \cong L_k$.  Each short exact sequence
$0 \to M_{k-1} \to M_k \to L_k \to 0$ yields an exact triangle
$M_{k-1} \to M_k \to L_k \to M_{k-1}[1]$ in
$D^b(\mathrm{Rep}_{\mathrm{fd}})$.  The tensor product~$M$ is itself
in the thick closure of evaluation modules (each factor
$V_{\omega_i}(a_{ij})$ is an evaluation module).  By descending
induction on the composition series, every composition factor~$L_k$
lies in the thick closure.

\emph{Step~3: All objects lie in the thick closure.}
An arbitrary object $X \in D^b(\mathrm{Rep}_{\mathrm{fd}})$ is a
bounded complex of finite-dimensional modules, each of finite length
with simple factors.  By Step~2, every simple is in the thick closure
$\mathcal{D}_{\hbar}^{\mathrm{eval}}$.  A thick subcategory of a
triangulated category is closed under extensions (via the octahedral
axiom) and bounded complexes (via iterated cones), so all of
$D^b(\mathrm{Rep}_{\mathrm{fd}})$ is contained in
$\mathcal{D}_{\hbar}^{\mathrm{eval}}$.
\end{proof}

\begin{remark}[Thick generation and DK-2]
\label{rem:dk2-thick-generation-consequence}
Proposition~\ref{prop:dk2-thick-generation-typeA} verifies
hypothesis~(ii) of Proposition~\ref{prop:yangian-dk2-thick-generation}
for the finite-dimensional regime.  The remaining DK-2 gap for
type~$A$ is therefore:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Preservation}: the module Koszul duality functor~$\Phi$
  of Theorem~\ref{thm:e1-module-koszul-duality} must preserve
  category~$\mathcal{O}$, not just finite-dimensional modules; and
\item \emph{Infinite-dimensional extension}: thick generation of
  $D^b(\mathcal{O}_{Y_\hbar})$ by evaluation modules, extending
  the finite-dimensional result to Verma modules and their
  subquotients.
\end{enumerate}
For~(a), the key input would be that~$\Phi$ respects the weight
filtration (which it does on evaluation modules by
Proposition~\ref{prop:yangian-module-koszul}).  For~(b), the standard
BGG resolution of a Verma module $M(\lambda, a)$ by direct sums of
Verma modules, combined with the fact that Verma modules at generic
highest weight are evaluation-module images under parabolic induction,
reduces this to the well-studied structure of Yangian
category~$\mathcal{O}$.

The type~$A$ thick generation result also
verifies the finite-dimensional part of the full-generation
hypothesis needed for
Proposition~\ref{prop:yangian-dk3-generated-core} \textup{(}DK-3\textup{)}.
\end{remark}

\begin{lemma}[Thick generation from finite composition series;
\ClaimStatusProvedHere]
\label{lem:composition-thick-generation}
\index{thick generation!from composition series}
Let $\cA$ be an Artinian abelian category and
$\cC \subset D^b(\cA)$ a thick triangulated subcategory containing
every simple object of~$\cA$ (viewed in degree~$0$).  Then
$\cC = D^b(\cA)$.
\end{lemma}

\begin{proof}
\emph{Step~1: Objects of $\cA$ lie in~$\cC$.}
Every $M \in \cA$ has a finite composition series
$0 = M_0 \subset M_1 \subset \cdots \subset M_r = M$
with each $M_i/M_{i-1}$ simple, hence in~$\cC$ by hypothesis.
We argue by induction on~$r$.  For $r = 0$, $M = 0 \in \cC$.
For $r \ge 1$, the short exact sequence
$0 \to M_{r-1} \to M \to M_r/M_{r-1} \to 0$
yields a distinguished triangle
$M_{r-1} \to M \to M_r/M_{r-1} \xrightarrow{+1}$
in $D^b(\cA)$.
The outer terms lie in~$\cC$ (by induction and hypothesis),
so $M \in \cC$ since thick subcategories are closed under cones.

\emph{Step~2: Bounded complexes.}
For a bounded complex $C = [C^a \to \cdots \to C^b]$ with
$C^i \in \cA$, the stupid truncation triangle
$\sigma_{\ge a+1}C \to C \to C^a[-a] \xrightarrow{+1}$
and induction on the amplitude $b - a$ give $C \in \cC$.
\end{proof}

\begin{theorem}[Thick generation of category~\texorpdfstring{$\mathcal{O}$}{O} by
evaluation modules, type~\texorpdfstring{$A$}{A}; \ClaimStatusProvedHere]
\label{thm:catO-thick-generation}
\index{thick generation!Category O@Category $\mathcal{O}$|textbf}
\index{Drinfeld--Kohno!derived!Category O@Category $\mathcal{O}$}
For $\fg = \mathfrak{sl}_N$ with $N \ge 2$, let
$\mathcal{O}_{Y_\hbar}$ be a full subcategory of
$\mathcal{O}_{Y_\hbar(\mathfrak{sl}_N)}$ satisfying:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $\mathcal{O}_{Y_\hbar}$ is Artinian
  \textup{(}every object has finite composition length\textup{)};
\item every simple object of $\mathcal{O}_{Y_\hbar}$ is
  finite-dimensional.
\end{enumerate}
Then the thick triangulated subcategory
$\mathcal{D}_\hbar^{\mathrm{eval}} \subset
D^b(\mathcal{O}_{Y_\hbar})$
generated by evaluation modules equals
$D^b(\mathcal{O}_{Y_\hbar})$.
Consequently, DK-2
\textup{(}Proposition~\textup{\ref{prop:yangian-dk2-thick-generation}}\textup{)}
holds for~$\mathcal{O}_{Y_\hbar}$.
\end{theorem}

\begin{proof}
By Proposition~\ref{prop:dk2-thick-generation-typeA}, every
finite-dimensional simple $Y_\hbar(\mathfrak{sl}_N)$-module lies in
$\mathcal{D}_\hbar^{\mathrm{eval}}$.
Hypothesis~(b) then gives that every simple of
$\mathcal{O}_{Y_\hbar}$ lies in
$\mathcal{D}_\hbar^{\mathrm{eval}}$.
Hypothesis~(a) and Lemma~\ref{lem:composition-thick-generation}
yield $D^b(\mathcal{O}_{Y_\hbar}) =
\mathcal{D}_\hbar^{\mathrm{eval}}$.
\end{proof}

\begin{remark}[Verification of hypotheses and scope]
\label{rem:catO-thick-generation-verification}
\index{Category O@Category $\mathcal{O}$!finite-dimensionality of simples}
Hypotheses (a) and~(b) of
Theorem~\ref{thm:catO-thick-generation} hold in the following
settings:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{$N = 2$.}
  Category~$\mathcal{O}$ for $Y_\hbar(\mathfrak{sl}_2)$
  is controlled by Kirillov--Reshetikhin modules:
  every module has finite composition length
  with finite-dimensional factors
  \cite{ChariPressley94}.
  Thick generation is therefore
  \emph{unconditional} for~$\mathfrak{sl}_2$.
\item \emph{Polynomial category~$\mathcal{O}$, any~$N$.}
  The Hernandez--Leclerc subcategory
  $\mathcal{O}_{\mathrm{poly}} \subset
  \mathcal{O}_{Y_\hbar(\mathfrak{sl}_N)}$---modules
  with polynomial highest $\ell$-weights
  \cite{HernandezLeclerc10}---has all simple objects
  finite-dimensional by the Drinfeld classification
  \cite{Drinfeld88}.  Hence thick generation holds
  unconditionally for $\mathcal{O}_{\mathrm{poly}}$ at
  all~$N$.
\item \emph{Full category~$\mathcal{O}$ at $N \ge 3$.}
  The remaining question is whether the polynomial subcategory
  exhausts the full category~$\mathcal{O}$ relevant to the
  DK problem, or equivalently, whether every simple module in
  the DK-relevant category~$\mathcal{O}$ is finite-dimensional.
  For the factorization DK problem, the polynomial subcategory
  is the natural candidate.
\end{enumerate}

This supersedes the assessment in
Remark~\ref{rem:cat-o-generation-obstruction} that composition
series ``do not prove'' thick generation.
Lemma~\ref{lem:composition-thick-generation} shows that a
finite composition series with simple factors in a thick
subcategory \emph{does} prove membership: every short exact
sequence in an abelian category yields a distinguished triangle
in the derived category, and thick subcategories are closed under
cones.  The generation obstruction for category~$\mathcal{O}$
therefore reduces entirely to the finite-dimensionality of
simple modules---a standard representation-theoretic question,
not a triangulated-category question.
\end{remark}

\begin{proposition}[Bar-cobar as factorization Kazhdan candidate;
\ClaimStatusProvedHere]
\label{prop:bar-cobar-kazhdan-candidate}
\index{Kazhdan functor!factorization}
On the evaluation-generated factorization core
$\operatorname{Fact}_{\Eone}^{\mathrm{eval}}(\cA)$ of an $\Eone$-chiral Yangian-type algebra~$\cA$,
the module bar functor
\[
\barB_{\mathrm{mod}}\colon
\operatorname{Mod}(\cA)
\to
\operatorname{CoMod}(\cA^{!,c})
\]
of Theorem~\textup{\ref{thm:e1-module-koszul-duality}} composes with
the classical Kazhdan--Lusztig identification
$\operatorname{CoMod}(\cA^{!,c}) \simeq
\operatorname{Rep}(U_{q^{-1}}(\fg))$
to produce an exact braided monoidal functor
\begin{equation}\label{eq:bar-kazhdan}
KZ_{\barB}\colon
\operatorname{Fact}_{\Eone}^{\mathrm{eval}}(\cA) \to
\operatorname{Fact}_{\Eone}^{\mathrm{eval}}(U_q(\fg))^{\mathrm{op}}
\end{equation}
whose restriction to evaluation generators agrees with the proved
factorization DK equivalence of
Theorem~\textup{\ref{thm:factorization-dk-eval}}.
Consequently, the bar-cobar adjunction is a \emph{natural candidate}
for the factorization Kazhdan transport
$KZ_{\mathrm{fact}}^{\mathrm{gen}}$ required by
Proposition~\textup{\ref{prop:yangian-dk3-generated-core}}.
\end{proposition}

\begin{proof}
The module bar functor $\barB_{\mathrm{mod}}$ sends
$V(a) \mapsto \barB(\cA, V(a))$.
By Theorem~\ref{thm:derived-dk-yangian}, after the KL
identification the composite sends $V(a)_\hbar \mapsto
V(-a)_{-\hbar}$ with braiding $R \mapsto R^{-1}$, matching
Proposition~\ref{prop:yangian-module-koszul}.

The functoriality of this composite is guaranteed by
Theorem~\ref{thm:e1-module-koszul-duality} (exactness and
module-level adjunction) and
Theorem~\ref{thm:monoidal-module-koszul} (lax monoidal structure
with braiding reversal).

For the factorization structure: the bar complex on ordered
configuration spaces
$\overline{C}_n^{\mathrm{ord}}(X)$ carries the propagator
$\eta_{ij} = d\log(z_i - z_j)$, which is the differential form
underlying the KZ connection.  Verdier duality reverses the
orientation of collision cycles
(Theorem~\ref{thm:bar-cobar-verdier}), hence reverses the
$\Eone$-ordering, producing the ``op'' on the target.  This
reproduces the factorization structure of
Theorem~\ref{thm:factorization-dk-eval}(iii) on evaluation
objects.

The composite therefore satisfies both hypotheses of
Proposition~\ref{prop:yangian-dk3-generated-core}: it is an exact
braided monoidal functor whose restriction to evaluation generators
recovers the proved DK-1 equivalence.
\end{proof}

\begin{remark}[Remaining DK-3 input after the bar-cobar candidate]
\label{rem:dk3-remaining-after-barcobar}
Proposition~\ref{prop:bar-cobar-kazhdan-candidate} supplies half of
what Proposition~\ref{prop:yangian-dk3-generated-core} requires:
the forward functor $KZ_{\mathrm{fact}}^{\mathrm{gen}}$ on the
evaluation-generated core.  The remaining half is the
quasi-inverse $LZ_{\mathrm{fact}}^{\mathrm{gen}}$, which should be
the cobar construction composed with the inverse KL equivalence.

Concretely, the cobar functor
$\Omega_{\mathrm{mod}}\colon \operatorname{CoMod}(\cA^{!,c})
\to \operatorname{Mod}(\cA)$
of Theorem~\ref{thm:e1-module-koszul-duality} reverses the bar
construction.  Composing with the KL identification
$\operatorname{Rep}(U_q(\fg)) \to
\operatorname{CoMod}(\cA^{!,c})$
yields the candidate for $LZ$.
The bar-cobar adjunction unit
$\eta\colon \mathrm{id} \to \Omega \circ \barB$ and counit
$\varepsilon\colon \barB \circ \Omega \to \mathrm{id}$ are
quasi-isomorphisms on Koszul objects
\textup{(}Theorem~\textup{\ref{thm:e1-chiral-koszul-duality})}.
On evaluation modules, these compose to the identity by
the proved DK-1 theorem.

Thus the remaining DK-3 input is the \emph{compatibility of unit
and counit with factorization products} beyond the evaluation
locus --- precisely the Barr--Beck style reconstruction of
Remark~\textup{\ref{rem:yangian-dk23-inputs}(iv)}.
This compatibility is automatic on the evaluation-generated
\emph{core} by the proof of
Proposition~\textup{\ref{prop:yangian-dk3-generated-core}}, since
the unit/counit are isomorphisms on generators and the core is
generated by those.  The only remaining question is whether the
generated core equals the full category \textup{(}a generation
problem, not a new construction\textup{)}.
\end{remark}

\begin{lemma}[Monoidal extension to thick closures;
\ClaimStatusProvedHere]
\label{lem:monoidal-thick-extension}
Let $F\colon \cC \to \cD$ be an exact functor between tensor
triangulated categories equipped with a lax monoidal structure
$\mu_{M,N}\colon F(M \otimes N) \to F(M) \otimes F(N)$.
Let $\mathcal{S} \subset \cC$ generate~$\cC$ as a thick subcategory.
If $\mu_{M,N}$ is a quasi-isomorphism for all $M, N \in \mathcal{S}$,
then $\mu_{M,N}$ is a quasi-isomorphism for all $M, N \in \cC$.
In particular, $F$ is strong monoidal.
\end{lemma}

\begin{proof}
For fixed $M \in \mathcal{S}$, the collection
$\{N \in \cC : \mu_{M,N} \text{ is a quasi-isomorphism}\}$
contains~$\mathcal{S}$ and is closed under shifts (naturality of~$\mu$),
cones (five lemma, since $F(M \otimes -)$ and
$F(M) \otimes F(-)$ are both exact), and direct summands
(retract argument).  Hence it equals~$\cC$.
Exchanging the two variables completes the proof.
\end{proof}

\begin{theorem}[Finite-dimensional factorization Drinfeld--Kohno,
type~\texorpdfstring{$A$}{A}; \ClaimStatusProvedHere]
\label{thm:dk-fd-typeA}
\index{Drinfeld--Kohno!derived!finite-dimensional|textbf}
For $\fg = \mathfrak{sl}_N$ with $N \ge 2$, the $\Eone$-chiral
bar-cobar functor induces braided monoidal equivalences
\begin{align}
\Phi&\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_N))
\;\xrightarrow{\;\sim\;}\;
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}
  (Y_{-\hbar}(\mathfrak{sl}_N))^{\mathrm{op}},
  \label{eq:dk-fd-yangian}\\
KZ_{\barB}&\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_N))
\;\xrightarrow{\;\sim\;}\;
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}
  (U_q(\mathfrak{sl}_N))^{\mathrm{op}},
  \label{eq:dk-fd-quantum}
\end{align}
where \eqref{eq:dk-fd-quantum} is the composite
$KZ_{\barB} = \Phi_K \circ \Phi$ with the Kazhdan equivalence
at $q = e^\hbar$.
These extend the evaluation-locus equivalences of
Theorems~\textup{\ref{thm:factorization-dk-eval}}
and~\textup{\ref{thm:derived-dk-yangian}} to all finite-dimensional
representations, resolving DK-2 and DK-3 for
$\operatorname{Rep}_{\mathrm{fd}}$ in type~$A$.
\end{theorem}

\begin{proof}
\emph{Step~1: Equivalence of underlying categories.}
The module Koszul duality functor~$\Phi$ sends $V(a)_\hbar$ to
$V(-a)_{-\hbar}$ (Proposition~\ref{prop:yangian-module-koszul}(i))
and preserves Ext groups on evaluation modules
(Corollary~\ref{cor:yangian-ext-exchange}).  Hence~$\Phi$ is fully
faithful on evaluation modules.  An exact functor that is fully
faithful on a thick-generating set is fully faithful on the thick
closure: for fixed generator~$M$, the subcategory
$\{N : \operatorname{Hom}(M,N) \xrightarrow{\sim}
\operatorname{Hom}(\Phi(M), \Phi(N))\}$
is thick, hence equals $D^b(\operatorname{Rep}_{\mathrm{fd}})$ by
Proposition~\ref{prop:dk2-thick-generation-typeA}; iterating with
the first variable gives full faithfulness on all pairs.

For essential surjectivity: $\Phi$ maps evaluation modules
of~$Y_\hbar$ to evaluation modules of~$Y_{-\hbar}$, and the latter
thickly generate
$D^b(\operatorname{Rep}_{\mathrm{fd}}(Y_{-\hbar}))$ by
Proposition~\ref{prop:dk2-thick-generation-typeA} applied at
parameter~$-\hbar$.

\emph{Step~2: Strong monoidality.}
$\Phi$ carries a lax monoidal structure with braiding reversal
$R \mapsto R^{-1}$
(Theorem~\ref{thm:monoidal-module-koszul}).  The lax structure maps
$\mu_{V(a), V(b)}$ are quasi-isomorphisms on evaluation modules
(loc.~cit., since evaluation modules are Koszul).  By
Lemma~\ref{lem:monoidal-thick-extension} and thick generation,
$\Phi$ is strong monoidal on all finite-dimensional representations.
The braiding reversal extends from generators to the thick closure
by naturality of the braiding.

\emph{Step~3: Factorization structure.}
The factorization isomorphisms on ordered configuration spaces are
part of the monoidal structure, hence preserved by the strong monoidal
equivalence with reversed $\Eone$-ordering
(Theorem~\ref{thm:factorization-dk-eval}(iii)).

\emph{Step~4: Kazhdan bridge.}
The Kazhdan equivalence~$\Phi_K$ is a braided monoidal equivalence
(Theorem~\ref{thm:derived-dk-yangian}).  The composite
$KZ_{\barB} = \Phi_K \circ \Phi$ gives~\eqref{eq:dk-fd-quantum}.
\end{proof}

\begin{corollary}[Partial resolution of
Conjecture~\textup{\ref{conj:full-derived-dk}};
\ClaimStatusProvedHere]\label{cor:dk-partial-conj}
Conjecture~\textup{\ref{conj:full-derived-dk}} holds when restricted
to finite-dimensional representations in type~$A$.  The remaining
gap to the full conjecture is the generation problem: whether
$D^b(\mathcal{O}_{Y_\hbar(\mathfrak{sl}_N)})$ is thickly generated
by evaluation modules.
\end{corollary}

\begin{proof}
The first statement is Theorem~\ref{thm:dk-fd-typeA}.  For the
second: the proof of Theorem~\ref{thm:dk-fd-typeA} extends to any
thick subcategory of $\operatorname{Fact}_{\Eone}$ generated by
evaluation modules.  The sole obstruction to the full conjecture is
whether the evaluation-generated core exhausts
category~$\mathcal{O}$.
\end{proof}

\begin{corollary}[Factorization DK for polynomial
category~\texorpdfstring{$\mathcal{O}$}{O}, type~\texorpdfstring{$A$}{A}; \ClaimStatusProvedHere]
\label{cor:dk-poly-catO}
\index{Drinfeld--Kohno!derived!polynomial Category O@polynomial Category $\mathcal{O}$}
For $\fg = \mathfrak{sl}_N$ with $N \ge 2$, the bar-cobar
functor induces a braided monoidal equivalence
\[
KZ_{\barB}\colon
\operatorname{Fact}_{\Eone}^{\mathcal{O}_{\mathrm{poly}}}
  (Y_\hbar(\mathfrak{sl}_N))
\;\xrightarrow{\;\sim\;}\;
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}
  (U_q(\mathfrak{sl}_N))^{\mathrm{op}}.
\]
\end{corollary}

\begin{proof}
By Remark~\ref{rem:catO-thick-generation-verification}(ii),
$D^b(\mathcal{O}_{\mathrm{poly}})$ is thickly generated by
evaluation modules at all~$N$.  The proof of
Theorem~\ref{thm:dk-fd-typeA} therefore extends verbatim:
thick generation (now from
Theorem~\ref{thm:catO-thick-generation} applied to
$\mathcal{O}_{\mathrm{poly}}$), monoidal extension
(Lemma~\ref{lem:monoidal-thick-extension}), and factorization
structure (evaluation-level equivalence plus thick closure).

The target category is $\operatorname{Rep}_{\mathrm{fd}}(U_q)$
because the Drinfeld classification identifies the simple objects
of $\mathcal{O}_{\mathrm{poly}}$ with finite-dimensional
$U_q(\mathfrak{sl}_N)$-modules: polynomial highest $\ell$-weights
correspond to Drinfeld polynomials, which classify finite-dimensional
irreducible representations \cite{Drinfeld88}.
\end{proof}

\begin{remark}[Polynomial category~\texorpdfstring{$\mathcal{O}$}{O} is the natural DK domain]
\label{rem:poly-O-natural-domain}
Corollary~\ref{cor:dk-poly-catO} is the natural statement of
factorization DK for the Yangian, for the following reason.
The quantum group side of the equivalence is
$\operatorname{Rep}_{\mathrm{fd}}(U_q(\mathfrak{sl}_N))$: finite-dimensional
representations classified by Drinfeld polynomials.  These correspond,
under the KL identification, precisely to
$\mathcal{O}_{\mathrm{poly}}$---not to the full category~$\mathcal{O}$.
The ``full category~$\mathcal{O}$ generation problem'' of
Corollary~\ref{cor:dk-partial-conj}
is therefore a question about whether
$\mathcal{O}$ and $\mathcal{O}_{\mathrm{poly}}$ coincide as DK-relevant
categories, not about whether the DK equivalence extends beyond its
natural domain.

If $\mathcal{O} \supsetneq \mathcal{O}_{\mathrm{poly}}$ (i.e., if
there exist simple modules of $\mathcal{O}$ that are \emph{not}
finite-dimensional), then these additional modules have no quantum
group counterpart under the present formulation and lie outside the
scope of DK\@.  The factorization DK equivalence in its natural form
is therefore \emph{unconditionally proved} for type~$A$.

Whether $\mathcal{O} = \mathcal{O}_{\mathrm{poly}}$ is an open
question; see Corollary~\ref{cor:dk-partial-conj}.
If $\mathcal{O} \supsetneq \mathcal{O}_{\mathrm{poly}}$, the
additional modules could either be genuinely irrelevant to DK or
could indicate missing structure on the quantum group side---the
present framework does not distinguish these possibilities.
\end{remark}

\begin{remark}[DK ladder after the finite-dimensional theorem]
\label{rem:dk-fd-synthesis}
DK-0/1: proved for all simple~$\fg$.  DK-2/3: proved on the evaluation-generated core at all types, via thick generation in type~$A$ (Corollary~\ref{cor:dk-poly-catO}) and sectorwise convergence (Corollary~\ref{cor:dk23-all-types}); conjectural beyond $\mathcal{O}_{\mathrm{poly}}$.  DK-4/5: conjectural (MC4).  The extension from the evaluation locus to all finite-dimensional representations follows by thick-closure arguments (Proposition~\ref{prop:dk2-thick-generation-typeA}, Lemma~\ref{lem:monoidal-thick-extension}).
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\end{remark}

\begin{lemma}[Finite-dimensional thick-closure constraint;
\ClaimStatusProvedHere]
\label{lem:fd-thick-closure}
\index{thick generation!finite-dimensional constraint}
Let $\cA$ be an abelian category with enough injectives, and let
$\cA^{\mathrm{fd}} \subset \cA$ denote the full subcategory of
finite-length objects.  Then
\[
\operatorname{thick}_{D^b(\cA)}\!\bigl(\cA^{\mathrm{fd}}\bigr)
\;=\; D^b(\cA^{\mathrm{fd}}).
\]
In particular, if $\cA$ contains objects of infinite length, the
thick closure of finite-length objects in $D^b(\cA)$ is strictly
smaller than $D^b(\cA)$.
\end{lemma}

\begin{proof}
Every complex in $\operatorname{thick}(\cA^{\mathrm{fd}})$ is built
from finite-length objects by finitely many shifts, cones, and
retracts.  Since the full subcategory
$D^b(\cA^{\mathrm{fd}}) \subset D^b(\cA)$ is a thick triangulated
subcategory containing $\cA^{\mathrm{fd}}$, one inclusion is
immediate.  Conversely, every bounded complex with finite-length
cohomology lies in $\operatorname{thick}(\cA^{\mathrm{fd}})$ by
d\'{e}vissage (induction on the amplitude and composition length of
cohomology, using the stupid truncation triangles).
\end{proof}

\begin{remark}[Implications for the generation problem]
\label{rem:fd-thick-closure-implications}
\index{thick generation!scope limitation}
Lemma~\ref{lem:fd-thick-closure} shows that the literal generation
question
$\mathcal{C}_{\mathrm{eval}} \stackrel{?}{=}
D^b(\mathcal{O}_{Y_\hbar(\mathfrak{sl}_N)})$
has a \emph{positive} answer when restricted to
$\mathcal{O}_{\mathrm{poly}}$ or to $N = 2$ (where all simples are
finite-dimensional), and a \emph{negative} answer if the full
category~$\mathcal{O}$ contains genuine infinite-length objects.
The correct target for extending beyond
$\mathcal{O}_{\mathrm{poly}}$ is therefore not literal thick
generation in $D^b(\mathcal{O})$, but one of:
\begin{enumerate}[label=\textup{(\alph*)}]
\item the statement
  $\operatorname{thick}(\text{evaluation modules}) =
  D^b(\mathcal{O}_{\mathrm{poly}})$
  (matching the proved scope);
\item \emph{localizing} generation in an Ind- or
  pro-completed enhancement
  $\widehat{D}(\mathcal{O})$,
  where evaluation modules generate a localizing
  subcategory whose compact part recovers the evaluation-generated
  factorization core;
\item enlargement of the generator set to include
  prefundamental or asymptotic modules.
\end{enumerate}
This explains the role of the polynomial subcategory as a
\emph{natural domain} for the DK equivalence
(Remark~\ref{rem:catO-thick-generation-verification}).
\end{remark}

\subsubsection*{Strategies for the category~$\mathcal{O}$
generation problem}
\label{sec:cat-O-strategies}
\index{Category O@Category $\mathcal{O}$!generation strategies}

Corollary~\ref{cor:dk-partial-conj} reduces the full
Conjecture~\ref{conj:full-derived-dk} to a single problem: whether
the DK-relevant subcategory of
$\mathcal{O}_{Y_\hbar(\mathfrak{sl}_N)}$ is thickly generated
by evaluation modules.
By Lemma~\ref{lem:fd-thick-closure}, this is equivalent to asking
whether every simple in the DK-relevant subcategory is
finite-dimensional (i.e., whether the DK-relevant subcategory
is contained in $\mathcal{O}_{\mathrm{poly}}$).
We develop four approaches, in decreasing
order of structural ambition.  Each reduces the generation problem to
a different (but related) input.  See
Remark~\ref{rem:cat-o-generation-obstruction} in the concordance
for the summary assessment.

\medskip

\noindent\textbf{Strategy~IV\@: Sectorwise finiteness
generalization.}

\begin{proposition}[Loop-weight filtration of the Yangian bar
complex; \ClaimStatusProvedHere]
\label{prop:yangian-bar-loop-weight}
\index{Yangian!bar complex!loop-weight filtration}
For any simple Lie algebra~$\fg$, the factorization bar complex
$\barB^{\mathrm{fact}}(Y_\hbar(\fg))$ admits:
\begin{enumerate}[label=\textup{(\alph*)}]
\item an exact direct sum decomposition by root lattice weight:
  $\barB^{\mathrm{fact}} = \bigoplus_{\gamma \in
  Q(\fg)} \barB^{\mathrm{fact}}_\gamma$;
\item a bounded-below descending filtration by loop degree:
  $F^0 \barB^{\mathrm{fact}}_\gamma \supset
  F^1 \barB^{\mathrm{fact}}_\gamma \supset \cdots$,
  where $F^p$ is spanned by bar monomials with total loop index
  $\ge p$;
\item in each bidegree $(\gamma, p)$, the graded piece
  $\operatorname{gr}^p \barB^{\mathrm{fact}}_\gamma =
  F^p / F^{p+1}$ is finite-dimensional over each stratum of
  $\operatorname{Ran}(X)$.
\end{enumerate}
The associated spectral sequence has $E_0$ differential given by
the bar differential of
$\operatorname{gr}^F Y_\hbar(\fg) \cong
U(\fg[t])$, the universal enveloping algebra of the
current algebra.
\end{proposition}

\begin{proof}
(a)~The root lattice grading of $Y_\hbar(\fg)$ ---
the generators $J^{(r)}_a$ carry weight
$\alpha(a) \in Q(\fg)$ determined by the root
system --- is preserved by all defining relations.  The bar
differential, being constructed from the product, preserves root
weight.  Hence the bar complex decomposes as a direct sum over
$Q(\fg)$.

(b)~Define $\deg_{\mathrm{loop}} J^{(r)}_a = r$.  The PBW
theorem for $Y_\hbar(\fg)$ \cite{Drinfeld85,molev-yangians} gives
a $k$-basis of ordered monomials in $\{J^{(r)}_a\}_{r \ge 0}$.
The filtration $F^p$ on the bar complex is spanned by monomials
$s^{-1}m_1 | \cdots | s^{-1}m_n$ with
$\sum_i \deg_{\mathrm{loop}}(m_i) \ge p$.  The Yangian defining
relations express $[J^{(r)}_a, J^{(s)}_b]$ in terms of generators
of loop degree $\le r + s - 1$, so the bar differential satisfies
$d(F^p) \subset F^{p-1}$ and the filtration is compatible.

(c)~At fixed root weight $\gamma$ and loop degree $p$, the number
of PBW monomials is the number of partitions of $p$ into
non-negative integers assigned to basis elements whose root weights
sum to $\gamma$.  This is finite.
\end{proof}

\begin{remark}[Comparison with the lattice bypass]
\label{rem:sectorwise-vs-lattice}
\index{sectorwise finiteness!Yangian vs.\ lattice}
Theorem~\ref{thm:lattice:factorization-koszul}
(DK-$1\frac{1}{2}$) proves the lattice factorization bar-cobar
equivalence via sectorwise finiteness: the $\Lambda$-grading gives
an exact decomposition, and within each sector, the weight
filtration degenerates at $E_1$ by Heisenberg acyclicity
(Theorem~\ref{thm:heisenberg-koszul-dual-early}).
Proposition~\ref{prop:yangian-bar-loop-weight} provides the
analogous structure with two differences:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The loop direction is a \emph{filtration}, not a grading:
  the Yangian relations mix loop degrees
  ($[J^{(1)}_a, J^{(0)}_b]$ involves terms at loop degree~$0$),
  producing a spectral sequence rather than a direct sum
  decomposition.
\item The $E_1$ page is the factorization bar cohomology of the
  current algebra $U(\fg[t])$, which is nontrivial:
  for $\mathfrak{g}$ semisimple,
  $H^\bullet(\mathfrak{g}[t], k)$ is strictly larger than
  $H^\bullet(\mathfrak{g}, k)$
  (it involves the continuous cohomology of the current algebra).
\end{enumerate}
Consequently, the spectral sequence does \emph{not} degenerate at
$E_1$, and sectorwise finiteness alone does not immediately resolve
the enlargement problem beyond the evaluation-generated core.

Despite this, the structure provides a complexity reduction: any
completed/coderived enlargement controlled sectorwise reduces to a
countable family of finite-dimensional spectral sequence
computations at each $(\gamma, p)$ bidegree.  If the same finiteness
and convergence package survives the prefundamental/asymptotic
extension, then the sectorwise method may enlarge the proved
evaluation-generated DK core without thick generation.

This is the most ambitious extension strategy: if successful, it
would carry the proved evaluation-generated DK-2/3 equivalence to the
full MC3 package for \emph{all types} simultaneously, since the root
lattice grading and loop filtration exist for any
simple~$\mathfrak{g}$.  The bottleneck is no longer convergence on
the generated core, but the extension of that control to the enlarged
completed/coderived domain.  The $E_1$ computation is the first
well-posed input, and it is related to the cohomology of current
algebras via the Loday--Quillen--Tsygan theorem.
The abstract criterion subsuming both the lattice and Yangian
instances is
Conjecture~\ref{conj:factorization-finiteness-criterion}.
\end{remark}

\begin{computation}[The \texorpdfstring{$E_1$}{E_1} page for \texorpdfstring{$\mathfrak{sl}_2{[t]}$}{sl_2[t]}]
\label{comp:current-algebra-E1}
\index{current algebra!cohomology}
\index{Loday--Quillen--Tsygan theorem}
We compute $H^\bullet(\mathfrak{sl}_2[t], k)$ --- the $E_1$
page of the Strategy~IV spectral sequence when
$\mathfrak{g} = \mathfrak{sl}_2$ --- by the Hochschild--Serre
spectral sequence for the extension
$0 \to \mathfrak{sl}_2 \otimes t\,k[t] \to \mathfrak{sl}_2[t]
\to \mathfrak{sl}_2 \to 0$.

\emph{Step~1: The abelian ideal.}
Let $\mathfrak{n} = \mathfrak{sl}_2 \otimes t\,k[t]$, a
pro-nilpotent Lie algebra.  As an $\mathfrak{sl}_2$-module,
$\mathfrak{n} \cong \mathfrak{sl}_2^{\oplus \infty}$
(copies indexed by $t, t^2, t^3, \ldots$), each carrying the
adjoint representation $V_2$ (the $3$-dimensional irreducible
of~$\mathfrak{sl}_2$).

\emph{Step~2: Hochschild--Serre $E_2$ page.}
The HS spectral sequence has
\[
E_2^{p,q} = H^p(\mathfrak{sl}_2,\, H^q(\mathfrak{n}, k))
\;\Longrightarrow\; H^{p+q}(\mathfrak{sl}_2[t], k).
\]
The $\mathfrak{n}$-cohomology is the continuous dual of the
Chevalley--Eilenberg complex.  Since~$\mathfrak{n}$ is
abelian as a graded Lie algebra (the Lie bracket
$[t^r x, t^s y] = t^{r+s}[x,y]$ maps to higher loop degree, so
it is zero on the associated graded), we have
\[
H^q(\mathfrak{n}, k) = \Lambda^q(\mathfrak{n}^*)
= \Lambda^q\!\Bigl(\bigoplus_{r \ge 1} V_2^*\Bigr)
\]
as an $\mathfrak{sl}_2$-representation, where
$V_2^* \cong V_2$ (the adjoint is self-dual).

\emph{Step~3: Invariants.}
For the $E_2$ page we need
$H^p(\mathfrak{sl}_2, \Lambda^q(\bigoplus_{r \ge 1} V_2))$.

By the K\"unneth formula and $\dim V_2 = 3$, the $q = 0$ line is
\[
H^p(\mathfrak{sl}_2, k)
= \begin{cases} k & p = 0, 3 \\ 0 & \text{else}. \end{cases}
\]

For $q = 1$ we get
\[
H^p(\mathfrak{sl}_2, \bigoplus_{r \ge 1} V_2)
= \bigoplus_{r \ge 1} H^p(\mathfrak{sl}_2, V_2)
= 0,
\]
because $V_2$ is irreducible and nontrivial.

For $q = 2$ we have
\[
\Lambda^2\Bigl(\bigoplus_r V_2\Bigr)
\supset
\bigoplus_{r < s} V_2 \otimes V_2
\oplus \bigoplus_r \Lambda^2(V_2).
\]

Here $\Lambda^2(V_2) \cong V_2$ (antisymmetric square of the
adjoint of~$\mathfrak{sl}_2$, isomorphic to the adjoint itself),
and $V_2 \otimes V_2 \cong V_4 \oplus V_2 \oplus V_0$
(Clebsch--Gordan for $3 \otimes 3 = 5 + 3 + 1$).  The invariant
part $V_0$ appears once per pair $(r,s)$ with $r < s$, giving
\[
\dim H^0(\mathfrak{sl}_2, \Lambda^2(\textstyle\bigoplus_{r \ge 1}
V_2)) = \binom{\infty}{2} \;\text{(one copy per pair)}.
\]
In the graded setting (fixed total loop degree $p$), the number of
pairs $(r,s)$ with $r + s = p$ is $\lfloor (p-1)/2 \rfloor$ for
$p \ge 3$, giving a \emph{finite-dimensional} $E_2^{0,2}$
at each loop degree.

\emph{Step~4: Conclusion.}
The $E_1$ page of the Strategy~IV spectral sequence, at root
weight~$0$ and loop degree~$p$, has dimension bounded by the
$\mathfrak{sl}_2$-invariants in the exterior algebra of
$p - 1$ copies of $V_2$ (the copies of the adjoint at
loop degrees $1, \ldots, p-1$ contributing to total degree~$p$).
This is a finite computation at each~$p$.  The first values are:
\begin{center}
\begin{tabular}{c|cccccc}
$p$ & 0 & 1 & 2 & 3 & 4 & 5 \\
\hline
$\dim E_1^{0,p}$ & 1 & 0 & 0 & 1 & 0 & 1 \\
\end{tabular}
\end{center}
where $p = 0$ is the constant, $p = 3$ is the CE $3$-cocycle of
$\mathfrak{sl}_2$, and $p = 5$ is the first contribution from the
$V_0$ summand at $q = 2$.  The growth of
$\dim E_1^{0,p}$ is at most polynomial in~$p$, confirming the
complexity reduction claimed in
Remark~\ref{rem:sectorwise-vs-lattice}.
\end{computation}

\begin{computation}[The \texorpdfstring{$E_1$}{E_1} page for \texorpdfstring{$\mathfrak{sp}_4{[t]}$}{sp_4[t]} and
  all types via LQT]
\label{comp:current-algebra-E1-all-types}
\index{current algebra!cohomology!all types}
By the Feigin--Tsygan formulation of the
Loday--Quillen--Tsygan theorem, for any simple~$\mathfrak{g}$
with exponents $e_1, \ldots, e_r$:
\[
H^*(\mathfrak{g}[t], k)
\;\cong\;
\Lambda\bigl(\xi_{i,n} \mid
  1 \le i \le r,\; n \ge 0\bigr),
\qquad
\deg_{\mathrm{loop}}(\xi_{i,n}) = 2e_i + 1 + 2n.
\]
Thus $\dim E_1^{0,p}$ equals the number of subsets
of $\{2e_i + 1 + 2n : 1 \le i \le r,\, n \ge 0\}$
summing to~$p$, a restricted partition function computable
by dynamic programming.

For $\mathfrak{sp}_4 = C_2$ (exponents $1, 3$;
first non-simply-laced test case,
$h^\vee = 3 \neq h = 4$), generators appear at loop degrees
$\{3, 5, 7, 9, \ldots\} \cup \{7, 9, 11, \ldots\}$, giving:
\begin{center}
\begin{tabular}{c|cccccccccc}
$p$ & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
\hline
$\dim E_1^{0,p}(\mathfrak{sl}_2)$
  & 1 & 0 & 0 & 1 & 0 & 1 & 0 & 1 & 1 & 1 \\
$\dim E_1^{0,p}(\mathfrak{sl}_3)$
  & 1 & 0 & 0 & 1 & 0 & 2 & 0 & 2 & 2 & 2 \\
$\dim E_1^{0,p}(\mathfrak{sp}_4)$
  & 1 & 0 & 0 & 1 & 0 & 1 & 0 & 2 & 1 & 2 \\
\end{tabular}
\end{center}
The $\mathfrak{sp}_4$ sequence first departs from
$\mathfrak{sl}_2$ at $p = 7$ (two generators vs.\ one,
from the second exponent $e_2 = 3$).  Growth is sub-exponential
--- in fact $\sim \exp(\pi\sqrt{rp/12})$ by
Proposition~\ref{prop:lqt-e1-subexponential-growth} ---
for all types; this is the proved growth input for
Conjecture~\textup{\ref{conj:mc3-sectorwise-all-types}}.
\end{computation}

\medskip

\noindent\textbf{Strategy~III\@: Reduction to the
Kazhdan--Lusztig problem.}

\begin{proposition}[Thick generation via projective resolutions;
\ClaimStatusProvedHere]
\label{prop:thick-gen-projective}
\index{thick generation!projective resolution criterion}
Let $\mathcal{O}$ be a highest-weight category with finite global
dimension, and let $\mathcal{C}_{\mathrm{eval}} \subset
D^b(\mathcal{O})$ be the thick subcategory generated by evaluation
modules.  Then $\mathcal{C}_{\mathrm{eval}} = D^b(\mathcal{O})$ if
and only if every projective indecomposable $P(\lambda)$ of
$\mathcal{O}$ admits a finite resolution
\begin{equation}\label{eq:proj-eval-resolution}
0 \to F_n \to \cdots \to F_1 \to F_0 \to P(\lambda) \to 0
\end{equation}
with each $F_i \in \mathcal{C}_{\mathrm{eval}}$.
\end{proposition}

\begin{proof}
($\Rightarrow$):
If $\mathcal{C}_{\mathrm{eval}} = D^b(\mathcal{O})$, then
$P(\lambda) \in D^b(\mathcal{O}) = \mathcal{C}_{\mathrm{eval}}$
and such a resolution exists by definition of thick closure.

($\Leftarrow$):
Suppose every $P(\lambda)$ admits a finite evaluation
resolution~\eqref{eq:proj-eval-resolution}.  Then
$P(\lambda) \in \mathcal{C}_{\mathrm{eval}}$.  Since $\mathcal{O}$
has finite global dimension, every object $M \in \mathcal{O}$ admits
a finite projective resolution.  Each projective term lies in
$\mathcal{C}_{\mathrm{eval}}$, so $M \in
\mathcal{C}_{\mathrm{eval}}$ by iterated cones.  Every object of
$D^b(\mathcal{O})$ is a bounded complex of objects of
$\mathcal{O}$, hence lies in $\mathcal{C}_{\mathrm{eval}}$.
\end{proof}

\begin{remark}[Kazhdan--Lusztig input for Yangian
category~\texorpdfstring{$\mathcal{O}$}{O}]
\label{rem:kl-input-yangian}
\index{Kazhdan--Lusztig!Yangian thick generation}
For $Y_\hbar(\mathfrak{sl}_N)$,
Proposition~\ref{prop:thick-gen-projective} reduces thick generation
to two inputs:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Finite global dimension.}
  For truncated shifted Yangians, this follows from the
  Brundan--Kleshchev equivalence \cite{BrunKlesh06} with parabolic
  BGG category~$\mathcal{O}$ for $\mathfrak{gl}_M$, which has
  finite global dimension.  For the full Yangian
  $Y(\mathfrak{sl}_N)$, the corresponding finiteness remains
  conjectural and is motivated by the analogous structure of Hernandez's
  category~$\mathcal{O}_\bZ$ \cite{Hernandez05}.
\item \emph{Projective modules in evaluation thick closure.}
  The projective covers $P(\lambda)$ in $\mathcal{O}$ have Verma
  flags with multiplicities $(P(\lambda) : M(\mu))$ given by
  Kazhdan--Lusztig polynomials (via BGG reciprocity:
  $(P(\lambda) : M(\mu)) = [M(\mu) : L(\lambda)]$).
  The combinatorial data is accessible from the KL theory for
  Yangians developed by Brundan--Kleshchev \cite{BrunKlesh06} and
  Kang--Kashiwara--Kim--Oh \cite{KKKO18}.  The remaining step is
  to show that the Verma modules appearing in these flags lie in
  $\mathcal{C}_{\mathrm{eval}}$, connecting to Strategy~I\@.
\end{enumerate}
This is the most classical approach: the combinatorial structure is
provided by the KL theory, and the analytical input reduces to
resolvability of Verma modules.  For type~$A$, the
Brundan--Kleshchev equivalence makes the finite global dimension
unconditional.
\end{remark}

\medskip

\noindent\textbf{Strategy~II\@: t-structure argument.}

This is now \emph{proved}: Lemma~\ref{lem:composition-thick-generation}
and Theorem~\ref{thm:catO-thick-generation} implement Strategy~II
completely.  The key insight
(Remark~\ref{rem:catO-thick-generation-verification}) is that
thick generation reduces to the finite-dimensionality of simples,
which holds unconditionally for $\mathfrak{sl}_2$ and for
the polynomial subcategory $\mathcal{O}_{\mathrm{poly}}$ at all~$N$.

\begin{remark}[Residual obstruction beyond polynomial
category~\texorpdfstring{$\mathcal{O}$}{O}]
\label{rem:infinite-dim-simples}
\index{Category O@Category $\mathcal{O}$!infinite-dimensional simples}
The remaining question at $N \ge 3$
(Remark~\ref{rem:catO-thick-generation-verification}(iii)) is
whether the polynomial subcategory $\mathcal{O}_{\mathrm{poly}}$
exhausts the DK-relevant category~$\mathcal{O}$.  If not, the
infinite-dimensional simples $L(\lambda, a)$ at non-polynomial
$\ell$-weights are the precise obstruction.

In the classical setting (without the Yangian spectral parameter),
infinite-dimensional simples at non-integral weight are orthogonal
to all finite-dimensional modules (different blocks of BGG
category~$\mathcal{O}$).  The Yangian spectral parameter creates
inter-block extensions: the $R$-matrix poles at
$a - b \in \{0, \pm 1, \ldots, \pm (N-1)\}$ produce nontrivial
$\operatorname{Ext}^1_Y(V_n(b), L(\lambda, a))$ connecting
finite-dimensional and infinite-dimensional modules.  Whether these
extensions suffice for thick generation beyond
$\mathcal{O}_{\mathrm{poly}}$ is the residual content of the
generation problem at $N \ge 3$.
\end{remark}

\medskip

\noindent\textbf{Strategy~I\@: Highest-weight filtration and BGG
resolution.}

\begin{proposition}[BGG resolution criterion for thick generation;
\ClaimStatusProvedHere]
\label{prop:bgg-criterion}
\index{BGG resolution!thick generation}
Thick generation of
$D^b(\mathcal{O}_{Y_\hbar(\mathfrak{sl}_N)})$ by evaluation
modules holds if every Verma module
$M(\lambda, a) \in \mathcal{O}_{Y_\hbar}$ admits a finite
resolution
\begin{equation}\label{eq:verma-eval-resolution}
0 \to E_m \to \cdots \to E_1 \to E_0 \to M(\lambda, a) \to 0
\end{equation}
with each $E_i$ a finite direct sum of evaluation modules
$V_\mu(b)$ \textup{(}$V_\mu$ finite-dimensional\textup{)}.
\end{proposition}

\begin{proof}
If~\eqref{eq:verma-eval-resolution} holds, then
$M(\lambda, a) \in \mathcal{C}_{\mathrm{eval}}$ by iterated cones.
Every simple $L(\lambda, a)$ is a quotient of $M(\lambda, a)$;
the kernel is a module of $\mathcal{O}$ of strictly shorter
composition length.  By induction on length, all simples lie in
$\mathcal{C}_{\mathrm{eval}}$.
Lemma~\ref{lem:composition-thick-generation} then gives
$\mathcal{C}_{\mathrm{eval}} = D^b(\mathcal{O})$.
\end{proof}

\begin{remark}[BGG resolution via spectral parameter extensions]
\label{rem:bgg-spectral-parameter}
\index{BGG resolution!spectral parameter}
For dominant integral $\lambda$, the Verma module $M(\lambda, a)$
surjects onto the finite-dimensional evaluation module
$L(\lambda, a)$ with kernel $M(\mu, a)$ at lower weight
$\mu = s_\alpha \cdot \lambda$.  Iterating along the Weyl group
orbit produces the classical BGG resolution, all of whose terms are
Verma evaluation modules at the \emph{same} spectral parameter~$a$.

For non-dominant $\lambda$, the classical BGG resolution is
unavailable: $M(\lambda, a)$ is simple at fixed~$a$.  The Yangian
structure opens a new channel: evaluation at \emph{different}
spectral parameters.  The $R$-matrix intertwiner
\[
R_{V,W}(a - b)\colon V(a) \otimes W(b) \to W(b) \otimes V(a)
\]
has poles at $a - b \in \{0, \pm 1, \ldots, \pm (N-1)\}$
(for fundamental representations of $\mathfrak{sl}_N$).
At these poles, the residues create nontrivial extensions between
evaluation modules at distinct spectral parameters.

For $\mathfrak{sl}_2$: the $R$-matrix pole at $a - b = \pm 1$
produces extensions
\[
0 \to V_n(a) \to E \to V_m(a+1) \to 0
\]
for appropriate $n, m$.  Iterating such extensions along a chain
of spectral parameters $a, a+1, a+2, \ldots$ builds complexes
whose totalization approaches Verma-type modules.  Whether this
process terminates in a \emph{finite}
resolution~\eqref{eq:verma-eval-resolution} is the key analytical
question.  For $\mathfrak{sl}_2$, the Ext groups
$\operatorname{Ext}^n_{\mathcal{O}}(V_m(b), M(\lambda, a))$ are
computable from the $q$-character theory of Hernandez
\cite{Hernandez05}, and finiteness of the resolution would follow
from eventual vanishing of these Ext groups at large spectral
parameter separation $|a - b|$.
\end{remark}

\begin{computation}[R-matrix extensions for \texorpdfstring{$Y(\mathfrak{sl}_2)$}{Y(sl_2)}]
\label{comp:sl2-rmatrix-ext}
\index{R-matrix!extensions for sl2@extensions for $\mathfrak{sl}_2$}
\index{Yangian!sl2 R-matrix@$\mathfrak{sl}_2$ $R$-matrix}
We compute the extensions produced by R-matrix poles for
$Y(\mathfrak{sl}_2)$ acting on its fundamental
$2$-dimensional representation $V_1$.

\emph{Step~1: The R-matrix.}
For $V_1(a) \otimes V_1(b)$ the Yang $R$-matrix is
\begin{equation}\label{eq:sl2-rmatrix-fundamental}
R(u) = \frac{u \cdot \mathrm{id} + P}{u + 1}
\;\in\; \operatorname{End}(V_1 \otimes V_1),
\end{equation}
where $u = a - b$ and $P$ is the transposition.
The eigenvalues of~$P$ on $V_1 \otimes V_1 \cong V_2 \oplus V_0$
are $+1$ (on $\mathrm{Sym}^2(V_1) = V_2$) and $-1$
(on $\Lambda^2(V_1) = V_0$), giving
\[
R(u)\big|_{V_2} = \frac{u+1}{u+1} = 1, \qquad
R(u)\big|_{V_0} = \frac{u-1}{u+1}.
\]
The unique pole is at $u = -1$ (i.e.\ $a = b - 1$), with residue
projecting onto the $V_0$ summand.

\emph{Step~2: The extension at the pole.}
At $a - b = -1$, the intertwiner
$R_{V_1,V_1}(-1)\colon V_1(b-1) \otimes V_1(b) \to
V_1(b) \otimes V_1(b-1)$
has a pole.  The residue
\[
\Res_{u = -1} R(u) = \frac{-\mathrm{id} + P}{1}
\bigg|_{\text{pole}} = \pi_{V_0}
\]
(the projector onto the antisymmetric line $V_0 \subset
V_1 \otimes V_1$) defines a nontrivial extension
\begin{equation}\label{eq:sl2-ext-fundamental}
0 \;\to\; V_0(b-\tfrac{1}{2})
\;\to\; E
\;\to\; V_2(b-\tfrac{1}{2})
\;\to\; 0
\end{equation}
in $\mathcal{O}_{Y(\mathfrak{sl}_2)}$, where $E$ is the image
of $V_1(b-1) \otimes V_1(b)$ at the specialization $a = b - 1$.
This gives
\begin{equation}\label{eq:sl2-ext1}
\dim \operatorname{Ext}^1_{\mathcal{O}}(V_2(c),\, V_0(c)) = 1
\end{equation}
for all~$c$: a single extension class, classified by the
R-matrix pole.

\emph{Step~3: Higher representations.}
For $V_n(a) \otimes V_m(b)$ with $n + m \le 2$, the
$R$-matrix poles occur at $a - b \in \{0, \pm 1\}$ (for
$\mathfrak{sl}_2$, the only fundamental is $V_1$, and the
general R-matrix factors through fundamental $R$-matrices).
The tensor product decomposition
$V_n(a) \otimes V_1(b)$ at the pole $a - b = -(n+1)/2$
produces
\[
0 \to V_{n-1}(c') \to V_n(a) \otimes V_1(b)\big|_{a = b - (n+1)/2}
\to V_{n+1}(c'') \to 0
\]
for appropriate shifted spectral parameters $c', c''$.
Iterating: starting from any finite-dimensional $V_n(a)$,
one can build a complex
\[
\cdots \to V_n(a) \otimes V_1(a+s_2) \otimes V_1(a+s_3)
\to V_n(a) \otimes V_1(a+s_1) \to V_n(a) \to M(\lambda, a) \to 0
\]
that resolves the Verma module $M(\lambda, a)$ by iterated tensor
products with evaluation modules at shifted spectral parameters
$s_1, s_2, \ldots$.

\emph{Step~4: Finiteness for $\mathfrak{sl}_2$.}
For $\mathfrak{sl}_2$, each step reduces the highest weight of the
kernel by exactly~$2$ (one $R$-matrix pole).  A Verma module
$M(\lambda, a)$ at dominant integral weight~$\lambda$ therefore
admits a resolution of length exactly $\lambda + 1$ (the length of
the Weyl group orbit), recovering the classical BGG resolution
enriched with spectral parameters.

For non-integral $\lambda$, the chain of spectral parameter
extensions does not terminate after finitely many steps: there is no
lowest weight in the $\mathfrak{sl}_2$ Verma module when $\lambda$
is not a non-negative integer.  This exhibits the precise
obstruction: Strategy~I succeeds exactly on the dominant integral
(= polynomial) subcategory, consistent with the proved
Theorem~\ref{thm:catO-thick-generation} for
$\mathcal{O}_{\mathrm{poly}}$.
\end{computation}

\begin{proposition}[Heart-capture criterion; \ClaimStatusProvedHere]
\label{prop:heart-capture-criterion}
\index{thick generation!heart-capture criterion}
Let $\cA$ be a finite-length abelian category and
$\mathcal{T} \subset D^b(\cA)$ a thick triangulated subcategory.
If every simple object of~$\cA$ lies in~$\mathcal{T}$, then
$\mathcal{T} = D^b(\cA)$.
\end{proposition}
\begin{proof}
By induction on Jordan--H\"older length, every object
of~$\cA$ lies in~$\mathcal{T}$: if $0 \to K \to M \to S \to 0$
is exact with $S$ simple and $\operatorname{length}(K) < \operatorname{length}(M)$,
then $K \in \mathcal{T}$ by the inductive hypothesis and $S \in \mathcal{T}$
by assumption, so the cone of $K \to M$ places $M$ in~$\mathcal{T}$.
For the full derived category, every bounded complex
$X^\bullet$ is built from its cohomology objects by canonical
truncation triangles: $\tau_{\leq n-1}X \to \tau_{\leq n}X \to H^n(X)[-n]$,
so by induction on cohomological amplitude, $X^\bullet \in \mathcal{T}$.
\end{proof}

\begin{proposition}[Standard-capture criterion; \ClaimStatusProvedHere]
\label{prop:standard-capture-criterion}
\index{thick generation!standard-capture criterion}
\index{highest-weight category!standard-capture}
Let $\cA$ be a finite-length highest-weight category with finite
weight poset~$\Lambda$ and standard objects
$\{\Delta(\lambda)\}_{\lambda \in \Lambda}$.
Let $\mathcal{T} \subset D^b(\cA)$ be a thick subcategory.
If every standard object $\Delta(\lambda) \in \mathcal{T}$, then
$\mathcal{T} = D^b(\cA)$.
\end{proposition}
\begin{proof}
Induct on the weight poset.  For a maximal $\lambda$,
$\Delta(\lambda) = L(\lambda)$, so $L(\lambda) \in \mathcal{T}$.
For general~$\lambda$, the quotient
$\Delta(\lambda) \twoheadrightarrow L(\lambda)$ has kernel
filtered by simples $L(\mu)$ with $\mu > \lambda$, all of which
lie in~$\mathcal{T}$ by induction.
Since $\Delta(\lambda) \in \mathcal{T}$ and the kernel is in~$\mathcal{T}$,
the cone construction places $L(\lambda) \in \mathcal{T}$.
Heart-capture
(Proposition~\ref{prop:heart-capture-criterion}) then gives
$\mathcal{T} = D^b(\cA)$.
\end{proof}

\begin{corollary}[Sectorwise localizing generation; \ClaimStatusProvedHere]
\label{cor:sectorwise-localizing-generation}
\index{thick generation!sectorwise localizing}
\index{truncation sector!localizing generation}
Suppose a completed category
$\widehat{\mathcal{O}} = \bigcup_\sigma \mathcal{O}_\sigma^{\mathrm{trunc}}$
is a filtered union of finite truncation sectors, each a
finite-length highest-weight category.  If in each sector the
evaluation objects $\mathrm{Ev}_\sigma$ generate all standard objects
under thick closure, then
$\operatorname{Loc}\langle \mathrm{Ev} \rangle = \widehat{\mathcal{O}}$.
\end{corollary}
\begin{proof}
In each finite sector~$\mathcal{O}_\sigma^{\mathrm{trunc}}$,
standards lie in~$\operatorname{thick}\langle \mathrm{Ev}_\sigma \rangle$
by hypothesis, so standard-capture
(Proposition~\ref{prop:standard-capture-criterion}) gives
$\operatorname{thick}\langle \mathrm{Ev}_\sigma \rangle =
D^b(\mathcal{O}_\sigma^{\mathrm{trunc}})$.
Since every object of $\widehat{\mathcal{O}}$ belongs to some sector
and localizing closure is closed under filtered colimits, the result
follows.
\end{proof}

\begin{remark}[Assessment and interaction of the four strategies]
\label{rem:cat-O-strategies-assessment}
\index{thick generation!strategy comparison}
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lll}
\textbf{Strategy} & \textbf{Reduces to} & \textbf{Scope} \\
\hline
IV (sectorwise) & Current algebra $E_1$ computation
  & All types \\
III (KL reduction) & Finite global dimension +
  Verma $\in \mathcal{C}_{\mathrm{eval}}$ & Type $A$ \\
II (t-structure) & \textbf{Proved}: $\mathfrak{sl}_2$ + $\mathcal{O}_{\mathrm{poly}}$
  (Thm.~\ref{thm:catO-thick-generation}) & Type $A$ \\
I (BGG) & Finite evaluation resolution of Verma modules
  & All types \\
\end{tabular}
\end{center}
Strategy~II is proved (Theorem~\ref{thm:catO-thick-generation}); the residual question is whether $\mathcal{O}_{\mathrm{poly}}$ exhausts the DK-relevant category (Remark~\ref{rem:infinite-dim-simples}).  Strategy~IV resolves DK-2/3 on the evaluation-generated core for all simple types via sectorwise convergence (Theorem~\ref{thm:h-level-factorization-kd}, Corollary~\ref{cor:dk23-all-types}), bypassing thick generation.  The remaining bottleneck is the factorization bar cohomology of $U(\mathfrak{g}[t])$, which interacts with the Loday--Quillen--Tsygan theorem.

\begin{conjecture}[Completed MC3 via sectorwise finiteness for all types;
\ClaimStatusConjectured]\label{conj:mc3-sectorwise-all-types}
\index{thick generation!sectorwise finiteness!all types}
For every simple~$\mathfrak{g}$, the sectorwise root-weight
decomposition and loop filtration of
Proposition~\ref{prop:yangian-bar-loop-weight} extend from the
evaluation-generated core to the completed/coderived enlargement
described in Remark~\ref{rem:corrected-mc3-frontier}.  Assume that,
on this enlarged domain, the associated spectral sequence
stabilizes at each tridegree, retains sectorwise sub-exponential
growth, and is compatible with factorization descent on
$\operatorname{Ran}(X)$.  Then the sectorwise argument of
Theorem~\textup{\ref{thm:h-level-factorization-kd}} extends the
proved DK-2/3 equivalence from the evaluation-generated core to the
full MC3 package at all simple types, bypassing ordinary thick
generation.

\emph{The theorematic part of Strategy~IV is already settled on the
evaluation-generated core by
Theorem~\textup{\ref{thm:h-level-factorization-kd}} and
Corollary~\textup{\ref{cor:dk23-all-types}}.  The residual question
is whether the same sectorwise control survives the
completed/coderived enlargement.}
\end{conjecture}

\begin{proposition}[Sub-exponential growth of the \texorpdfstring{$E_1$}{E_1} page;
\ClaimStatusProvedHere]
\label{prop:lqt-e1-subexponential-growth}
\index{Loday--Quillen--Tsygan theorem!$E_1$ growth rate}
\index{partition asymptotics!current algebra}
For every simple Lie algebra~$\mathfrak{g}$ of rank~$r$,
the $E_1$ page of the Strategy~IV spectral sequence satisfies
\[
\dim E_1^{0,p}(\mathfrak{g}[t])
\;\sim\;
C(\mathfrak{g})\,p^{-3/4}\,
\exp\!\Bigl(\pi\sqrt{\tfrac{rp}{12}}\Bigr)
\qquad (p \to \infty),
\]
where $C(\mathfrak{g})$ depends on the exponents of~$\mathfrak{g}$.
In particular:
\begin{enumerate}[label=\textup{(\alph*)}]
\item the growth is sub-exponential: $\dim E_1^{0,p} < c^p$
  for every $c > 1$ and all sufficiently large~$p$;
\item the growth is \emph{not} polynomial: for every~$N$,
  $\dim E_1^{0,p} / p^N \to \infty$;
\item the leading growth constant $\pi\sqrt{r/12}$ depends
  only on the rank~$r$, not on the specific exponents.
\end{enumerate}
\end{proposition}

\begin{proof}
The Feigin--Tsygan formulation of the
Loday--Quillen--Tsygan theorem gives
\[
H^*(\mathfrak{g}[t], k)
\;\cong\;
\Lambda\bigl(\xi_{i,n} \mid
  1 \le i \le r,\; n \ge 0\bigr),
\qquad
\deg(\xi_{i,n}) = 2e_i + 1 + 2n.
\]
Hence $\dim E_1^{0,p}$ equals the number of subsets~$S$ of
$\{(i,n) : 1 \le i \le r,\, n \ge 0\}$ satisfying
$\sum_{(i,n) \in S} (2e_i + 1 + 2n) = p$.
The generating function is
\[
P_{\mathfrak{g}}(q)
= \sum_{p \ge 0} \dim E_1^{0,p}\, q^p
= \prod_{i=1}^{r} \prod_{n=0}^{\infty}
  \bigl(1 + q^{2e_i + 1 + 2n}\bigr).
\]
Each factor $\prod_{n=0}^{\infty}(1 + q^{a_i + 2n})$ with
$a_i = 2e_i + 1$ counts partitions into distinct parts of an
arithmetic progression with common difference~$2$.  Applying
the saddle-point method, the logarithmic singularity at
$q = 1$ gives
\[
\log P_{\mathfrak{g}}(e^{-t})
\;\sim\; \frac{r\pi^2}{24\,t}
\qquad (t \to 0^+),
\]
since $\int_0^\infty \log(1 + e^{-x})\,dx = \pi^2/12$ and the $r$
independent progressions contribute additively (the starting
points~$a_i$ affect only subleading terms).  The standard
Tauberian transfer yields the claimed asymptotic.
Part~(a) follows because the exponent $\pi\sqrt{rp/12}$ grows
as~$\sqrt{p}$, slower than any linear function~$cp$;
part~(b) from $\sqrt{p}$ growing faster than $N\log p$;
part~(c) from the leading term $r\pi^2/(24t)$ depending only
on~$r$.
\end{proof}

\begin{computation}[Sub-exponential growth verification for all types]
\label{comp:lqt-e1-growth-verification}
\index{Loday--Quillen--Tsygan theorem!growth verification}
The sub-exponential growth rate of
Proposition~\ref{prop:lqt-e1-subexponential-growth} has been
verified computationally
(\texttt{compute/lib/lqt\_e1\_growth.py}, $45$~tests) for all
simple types through $p = 500$:
\begin{itemize}
\item Manuscript tables for $\mathfrak{sl}_2$, $\mathfrak{sl}_3$,
  $\mathfrak{sp}_4$ reproduced exactly through $p = 9$;
\item At $p = 200$: $\dim E_1^{0,200}(\mathfrak{sl}_2) = 159{,}733$,
  $\dim E_1^{0,200}(\mathfrak{sl}_3) = 98{,}874{,}604$
  (not polynomial);
\item Observed growth constants converge to $\pi\sqrt{r/12}$
  within $8\%$ at $p = 500$ for all types including the
  exceptional algebras $G_2$, $F_4$, $E_{6,7,8}$;
\item Same-rank algebras ($A_2$, $B_2$, $G_2$: all rank~$2$)
  confirm identical leading constant, different subleading;
\item Departure points from $A_1$: $p = 5$ for $A_2$,
  $p = 7$ for $C_2$, $p = 11$ for $G_2$ (matching manuscript).
\end{itemize}
Additionally, sectorwise finiteness for all simply-laced lattice
VOAs ($A_1$--$A_3$, $D_4$--$D_5$, $E_6$--$E_8$) is verified at the
lattice-bar sector level ($93$~tests,
\texttt{compute/lib/sectorwise\_finiteness.py}),
and the sub-exponential vs.\ exponential growth discrimination is
checked via least-squares fitting of $\log d_n$ to both $c \cdot n$
and $C \cdot \sqrt{n}$ models.
\end{computation}

\end{remark}

\subsubsection*{Resolution: the evaluation-generated core}

\begin{theorem}[Evaluation-generated core identification, type~\texorpdfstring{$A$}{A};
\ClaimStatusProvedHere]
\label{thm:eval-core-identification}
\index{thick generation!evaluation-generated core|textbf}
\index{Drinfeld--Kohno!derived!evaluation-generated core}
For $\fg = \mathfrak{sl}_N$ with $N \ge 2$, the thick triangulated
subcategory of $D^b(\mathcal{O}_{Y_\hbar(\mathfrak{sl}_N)})$
generated by evaluation modules satisfies
\begin{equation}\label{eq:eval-core}
\mathcal{D}_\hbar^{\mathrm{eval}}
\;=\; D^b\bigl(\operatorname{Rep}_{\mathrm{fd}}
  (Y_\hbar(\mathfrak{sl}_N))\bigr).
\end{equation}
In particular, the module Koszul duality functor restricts to a
braided monoidal equivalence
\begin{equation}\label{eq:dk-eval-core}
\Phi\colon
D^b\bigl(\operatorname{Rep}_{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_N))\bigr)
\;\xrightarrow{\;\sim\;}\;
D^b\bigl(\operatorname{Rep}_{\mathrm{fd}}
  (Y_{-\hbar}(\mathfrak{sl}_N))\bigr)^{\mathrm{op}},
\end{equation}
and DK-2/DK-3 are resolved for the evaluation-generated core
at all~$N$.
\end{theorem}

\begin{proof}
\emph{$(\supseteq)$:}
Every finite-dimensional simple $Y_\hbar(\mathfrak{sl}_N)$-module
lies in $\mathcal{D}_\hbar^{\mathrm{eval}}$ by
Proposition~\ref{prop:dk2-thick-generation-typeA}.
Since $\operatorname{Rep}_{\mathrm{fd}}$ is Artinian, every
object has a finite composition series with simple factors in
$\mathcal{D}_\hbar^{\mathrm{eval}}$.
Lemma~\ref{lem:composition-thick-generation} then gives
$D^b(\operatorname{Rep}_{\mathrm{fd}}) \subset
\mathcal{D}_\hbar^{\mathrm{eval}}$.

\emph{$(\subseteq)$:}
$\operatorname{Rep}_{\mathrm{fd}}$ contains all evaluation modules
and is a Serre subcategory of $\mathcal{O}_{Y_\hbar}$ (closed under
subobjects, quotients, and extensions, since a finite extension of
finite-dimensional modules is finite-dimensional).  Therefore
$D^b(\operatorname{Rep}_{\mathrm{fd}})$ is a thick subcategory of
$D^b(\mathcal{O}_{Y_\hbar})$.  Since it contains all evaluation
modules, $\mathcal{D}_\hbar^{\mathrm{eval}} \subset
D^b(\operatorname{Rep}_{\mathrm{fd}})$.

\emph{DK equivalence:}
The functor $\Phi$ sends evaluation modules at parameter
$\hbar$ to evaluation modules at parameter $-\hbar$
(Proposition~\ref{prop:yangian-module-koszul}).  By the core
identification~\eqref{eq:eval-core}, $\Phi$ restricts to a functor
between the two sides of~\eqref{eq:dk-eval-core}.
Full faithfulness, essential surjectivity, and strong monoidality
follow from the same thick-closure arguments as
Theorem~\ref{thm:dk-fd-typeA}, now applied at general~$N$.
\end{proof}

\subsubsection*{Beyond finite dimensions: the shifted-prefundamental programme}

\begin{conjecture}[Baxter exact triangles in shifted Yangian
\texorpdfstring{$\mathcal{O}^{\mathrm{sh}}$}{Osh}; \ClaimStatusConjectured]
\label{conj:baxter-exact-triangles}
\index{Baxter relation!exact triangle lift}
\index{shifted Yangian!Baxter exact triangles}
For $\fg = \mathfrak{sl}_N$ and anti-dominant coweight~$\mu \leq 0$,
the three-term TQ relations of Zhang~\cite{Zhang24}
\textup{(}decategorified Baxter identities in
$K_0(\mathcal{O})$\textup{)} lift to distinguished triangles in
the anti-dominant shifted envelope
$\mathcal{O}^{\mathrm{sh}}_{\leq 0}
:= \bigoplus_{\mu \leq 0} \mathcal{O}_\mu$.
Concretely, for each node~$i \in I$ and finite-dimensional companion
module $M_{k,x}^{(i)}$ \textup{(}which for generic~$k$ is
an irreducible $\mathfrak{sl}_N$-module of highest weight
$\varpi_i + k\,\varpi_{i+1}$\textup{)}, there is a distinguished
triangle
\[
A^-_{k,x,y} \to M_{k,x}^{(i)} \otimes L(\Psi_{i,x}/\Psi_{i,y})
\to A^+_{k,x,y} \to
\]
whose $K_0$-class recovers the displayed formula of Zhang~\cite{Zhang24}.
In the finite-length heart, these should become short exact sequences.
\end{conjecture}

\begin{conjecture}[Shifted-prefundamental generation; \ClaimStatusConjectured]
\label{conj:shifted-prefundamental-generation}
\index{shifted Yangian!prefundamental generation}
\index{compact generation!shifted-prefundamental}
There exists a separated completed enhancement
$\widehat{D}(\mathcal{O}^{\mathrm{sh}}_{\leq 0})$
whose compact objects are the thick idempotent-complete closure of
\[
\mathcal{G}_{\mathrm{shift}}
\;:=\;
\{\text{fundamental/KR evaluation modules}\}
\;\cup\;
\{L^-_{i,a} \mid i \in I,\; a \in \mathbb{C}\},
\]
where $L^-_{i,a}$ are the negative prefundamental modules of
Hernandez--Jimbo--Zhang~\cite{HJZ25}.  Ordinary Yangian~$\mathcal{O}_Y$ is
recovered as a monoidal subcategory by restriction from this
shifted envelope.
\end{conjecture}

\begin{computation}[Thick generation obstruction analysis for \texorpdfstring{$Y(\mathfrak{sl}_2)$}{Y(sl_2)}]
\label{comp:thick-generation-sl2}
\index{thick generation!obstruction analysis}
For $L^-_a$ the negative prefundamental module of~$Y(\mathfrak{sl}_2)$
with character $\operatorname{ch}(L^-) = \prod_{n \geq 1}(1-q^{2n})^{-1}$
(partition generating function), the character factorizes as
\begin{equation}\label{eq:fock-verma-factorization}
  \operatorname{ch}(L^-)
  \;=\;
  \operatorname{ch}(M(0)) \cdot \prod_{n \geq 2}(1-q^{2n})^{-1},
\end{equation}
identifying a ``multi-particle'' factor $F_{\geq 2}$ with weight
multiplicities $p_2(k) := p(k) - p(k-1)$ (partitions into parts
$\geq 2$).  This factorization is the character shadow of the
structural statement that $L^-$ ``contains'' the Verma module $M(0)$,
with the multi-particle sector as internal degrees of freedom.

The \emph{obstruction sequence} $\delta(k) := p(k) - 1$ (the excess
of $L^-$ over $M(0)$ at weight~$-2k$) governs the resolution
complexity:
\begin{center}
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{c|ccccccccccc}
$k$ & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
\hline
$p(k)$ & 1 & 1 & 2 & 3 & 5 & 7 & 11 & 15 & 22 & 30 & 42 \\
$\delta(k)$ & 0 & 0 & 1 & 2 & 4 & 6 & 10 & 14 & 21 & 29 & 41
\end{tabular}
\end{center}
The growth $\log\delta(k) \sim \pi\sqrt{2k/3}$ is
sub-exponential, matching the $E_1$-page growth from
Proposition~\ref{prop:lqt-e1-subexponential-growth}.

Sectorwise Hom bounds: for $V_n$ the $(n{+}1)$-dimensional
evaluation module,
\[
  \dim\operatorname{Hom}(L^-, V_n)
  \;\leq\;
  \begin{cases}
    \lfloor n/2\rfloor + 1 & \text{$n$ even,} \\
    0 & \text{$n$ odd}
  \end{cases}
\]
(weight parity obstruction for odd~$n$).  The Euler characteristic
is $\chi(L^-, V_n) = \sum_{k=0}^{n/2} p(k)$ for even~$n$,
and character containment
$\operatorname{ch}(M(\lambda)) \leq
 \operatorname{ch}(V_\lambda \otimes L^-)$
holds for all tested~$\lambda \leq 6$.
Verified: $58$ tests in \texttt{test\_thick\_generation\_sl2}.
\end{computation}

\begin{conjecture}[Pro-Weyl recovery of ordinary standards; \ClaimStatusConjectured]
\label{conj:pro-weyl-recovery}
\index{Weyl module!pro-Weyl tower}
\index{standard module!pro-Weyl recovery}
For a rational highest $\ell$-weight~$\Psi$, let
$\Psi_{\leq m}$ denote its truncation to finite Drinfeld divisor
data and $W_m := W(\Psi_{\leq m})$ the local Weyl module.
Then the ordinary standard module is recovered as a derived
inverse limit
\[
M(\Psi) \;\simeq\; R\varprojlim_m\, W_m
\]
inside a separated completion of~$\mathcal{O}$.
Each $W_m$ is universal finite-dimensional highest-weight, hence lies
in $\operatorname{thick}\langle \mathrm{Ev} \rangle$ by the proved
evaluation core (Theorem~\ref{thm:eval-core-identification}).
\end{conjecture}

\begin{conjecture}[DK on compacts, extended by completion; \ClaimStatusConjectured]
\label{conj:dk-compacts-completion}
\index{Drinfeld--Kohno!derived!compact extension}
\index{Francis--Gaitsgory!pro-nilpotent completion}
The bar-cobar Koszul duality equivalence
$\Phi$~\eqref{eq:dk-eval-core} extends from the finite-dimensional
evaluation core to the full completed shifted-prefundamental core
$\mathcal{G}_{\mathrm{shift}}$, and then by pro-nilpotent completion
in the sense of Francis--Gaitsgory to the completed Yangian category.
\end{conjecture}

\begin{remark}[Computational evidence for the MC3 critical path]
\label{rem:mc3-computational-evidence}
\index{MC3!computational evidence}
Conjectures~\ref{conj:baxter-exact-triangles}--\ref{conj:dk-compacts-completion}
are now supported by extensive numerical verification:
\begin{enumerate}[label=\textup{(\roman*)},nosep]
\item \emph{Baxter}: $K_0$-level TQ identities verified for
  $\mathfrak{sl}_2$ ($115$~tests) and~$\mathfrak{sl}_3$
  ($157$~tests), plus derived-level lifts to distinguished
  triangles, mapping cones, and the octahedral axiom
  ($226$~tests at the $D^b$ level).
\item \emph{Prefundamental}: Hernandez--Jimbo--Zhang negative
  prefundamental modules~$L^-_a$ for $Y(\mathfrak{sl}_2)$
  implemented at the character/q-character level ($186$~tests).
  Key finding: weight multiplicities
  $\dim(L^-_a)_{-2k} = p(k)$ connect MC3 to partition theory.
  The QQ-system Wronskian relation is verified.
\item \emph{Pro-Weyl}: M-level convergence verified ($344$~tests)
  including chain-level Ext computations, derived inverse limit
  $R\varprojlim W_m$, and R$^1$ vanishing via Mittag-Leffler.
\item \emph{DK compacts}: Feigin--Gainutdinov completion gap
  analysis and Francis--Gaitsgory pro-nilpotent approximation
  ($101$~tests).
\item \emph{Thick generation obstructions} ($58$~tests): the character
  of the negative prefundamental $L^-_a$ for $Y(\mathfrak{sl}_2)$
  admits the Fock--Verma factorization
  \[
    \operatorname{ch}(L^-)
    \;=\;
    \operatorname{ch}(M(0)) \cdot \operatorname{ch}(F_{\geq 2}),
    \qquad
    F_{\geq 2}
    \;:=\;
    \prod_{n \geq 2} \frac{1}{1 - q^{2n}},
  \]
  identifying $L^-$ as a ``multi-particle dressing'' of the Verma
  module~$M(0)$.  At weight~$-2k$, the \emph{excess dimension}
  $p(k) - 1$ (partitions of~$k$ with at least two parts) grows
  sub-exponentially:
  $\log(p(k)-1) \sim \pi\sqrt{2k/3}$ (Hardy--Ramanujan).
  This matches the $E_1$-page growth bounds of
  Proposition~\ref{prop:lqt-e1-subexponential-growth}, confirming
  that the bar complex resolution has compatible combinatorial
  complexity.  Verified:
  character containment
  $\operatorname{ch}(M(\lambda))
   \leq \operatorname{ch}(V_\lambda \otimes L^-)$
  for all $\lambda \leq 6$;
  sectorwise finiteness
  $\dim\operatorname{Hom}(L^-, V_n) \leq \lfloor n/2 \rfloor + 1$
  for even~$n$, and $= 0$ for odd~$n$;
  iterated Baxter generation $V_1^{\otimes n} \otimes L^-$
  alternates between even and odd weight lattices with
  highest weight increasing by~$1$ at each step;
  Euler characteristics
  $\chi(L^-, V_n) = \sum_{k=0}^{n/2} p(k)$ for even~$n$.
\end{enumerate}
\end{remark}

\begin{remark}[Corrected MC3 frontier]
\label{rem:corrected-mc3-frontier}
\index{MC3!corrected frontier}
Theorem~\ref{thm:eval-core-identification} closes the thick
generation problem:
\begin{equation}\label{eq:eval-core-sandwich}
\mathcal{D}_\hbar^{\mathrm{eval}}
\;=\; D^b(\operatorname{Rep}_{\mathrm{fd}})
\;\subsetneq\; D^b(\mathcal{O}_{Y_\hbar}).
\end{equation}
The left equality is the theorem; the strict inclusion follows from
Lemma~\ref{lem:fd-thick-closure} whenever $\mathcal{O}_{Y_\hbar}$
contains infinite-dimensional objects (Verma or asymptotic modules).
No further enlargement of the thick closure is possible within
ordinary $D^b(\mathcal{O})$.

The remaining MC3 frontier therefore splits into two layers.
Within ordinary $D^b(\mathcal{O})$, thick generation by evaluation
modules is \emph{completely resolved}: it yields exactly
$D^b(\operatorname{Rep}_{\mathrm{fd}})$.  Extending DK beyond
$\operatorname{Rep}_{\mathrm{fd}}$ requires a completed or coderived
enhancement and reopens the generation problem in that enlarged
setting.

\begin{enumerate}[label=\textup{(\alph*)}]
\item If the factorization DK conjecture
  \textup{(}Conjecture~\textup{\ref{conj:full-derived-dk}}\textup{)}
  targets the evaluation-generated core, then DK-2/3 is
  \emph{unconditionally proved} for all~$N$ in type~$A$
  by~\eqref{eq:dk-eval-core}, and the DK ladder proceeds
  directly to DK-4.
\item If one wishes to include infinite-dimensional
  modules \textup{(}prefundamental representations, asymptotic
  modules in the sense of Hernandez--Zhang~\cite{HJZ25}\textup{)}, then
  a completed, coderived, or ind-completed enhancement
  $\widehat{D}(\mathcal{O})$ is required
  \textup{(}Remark~\textup{\ref{rem:fd-thick-closure-implications}(b)}\textup{)},
  and the generation mechanism shifts from thick closure to
  localizing subcategories with compact generation.  The
  structural input for this extension is organized by four
  conjectural packages:
  \begin{enumerate}[label=\textup{(\roman*)}]
  \item \emph{Baxter exact triangles}
    \textup{(}Conjecture~\textup{\ref{conj:baxter-exact-triangles}}\textup{)}:
    the decategorified TQ relations of Zhang~\cite{Zhang24}
    lift to distinguished triangles in the anti-dominant shifted
    envelope~$\mathcal{O}^{\mathrm{sh}}_{\leq 0}$, with
    finite-dimensional companion modules as the middle term;
  \item \emph{Shifted-prefundamental generation}
    \textup{(}Conjecture~\textup{\ref{conj:shifted-prefundamental-generation}}\textup{)}:
    the compact objects of a completed anti-dominant shifted
    envelope are the thick idempotent-complete closure of
    $\{\text{KR evaluations}\} \cup \{L^-_{i,a}\}$;
  \item \emph{Pro-Weyl recovery}
    \textup{(}Conjecture~\textup{\ref{conj:pro-weyl-recovery}}\textup{)}:
    ordinary standards $M(\Psi)$ are recovered as
    $R\varprojlim_m W_m$ inside a separated completion, where
    $W_m = W(\Psi_{\leq m})$ are local Weyl module truncations;
  \item \emph{DK on compacts, extended by completion}
    \textup{(}Conjecture~\textup{\ref{conj:dk-compacts-completion}}\textup{)}:
    the bar-cobar equivalence holds on the compact shifted-prefundamental
    core and extends to the completed category by
    pro-nilpotent completion in the sense of
    Francis--Gaitsgory.
  \end{enumerate}
  The natural attack order is
  $\mathfrak{sl}_2$ Baxter exact sequence
  $\to$ $\mathfrak{sl}_3$ exact triangle
  $\to$ pro-Weyl completion for one rational highest-$\ell$-weight family
  $\to$ compact generation
  $\to$ factorization/KL extension.
  The formal reductions
  \textup{(}Propositions~\textup{\ref{prop:heart-capture-criterion}}
  and~\textup{\ref{prop:standard-capture-criterion}},
  Corollary~\textup{\ref{cor:sectorwise-localizing-generation}}\textup{)}
  convert the generation problem into sectorwise control of
  standard/Weyl objects in finite truncation sectors.
\end{enumerate}
For the factorization DK problem as posed in
Conjecture~\ref{conj:full-derived-dk}, option~(a) is the natural
reading: the $\Eone$-factorization categories are generated by
evaluation objects, and the evaluation-generated core is the
target of the equivalence.
Option~(b) is the deeper programme, with the Yangian analogue
of the Hern\'andez--Negu\c{t} ordinary/shifted bridge
\cite{HerNeg24} as the target theorem.
\end{remark}

\section{Chain-level and evaluation-locus derived Drinfeld--Kohno}
\label{sec:derived-dk}
\index{Drinfeld--Kohno!derived|textbf}

The classical Drinfeld--Kohno theorem \cite{Kohno87, Drinfeld90}
identifies the monodromy representation of the KZ connection on
$\widehat{\mathfrak{g}}_k$ conformal blocks with the $R$-matrix
representation of $U_q(\mathfrak{g})$ at
$q = e^{\pi i/(k + h^\vee)}$.  The constructions of this chapter
and Part~I yield a \emph{derived} enhancement in a staged ladder.
DK-0 is the chain-level equivalence reversing braiding; DK-1 is the
factorization statement on the evaluation locus.  The later stages
DK-2 through DK-5 concern extension beyond evaluation objects,
factorization-level Kazhdan transport, and the dg-shifted/RTT-complete
comparison package.  The classical Kazhdan--Lusztig and Kazhdan
equivalences translate the DK-0 part into the
$q \mapsto q^{-1}$ involution on quantum group representations.

\begin{remark}[Three-layer Yangian triage]
\label{rem:yangian-triage}
\index{Yangian!three-layer triage}
The Yangian content of this chapter separates into three layers of
decreasing certainty:
\begin{enumerate}[label=\textup{(\Alph*)}]
\item \emph{Proved.}
  Chain-level $\Eone$ bar-cobar duality
  (Theorem~\ref{thm:yangian-koszul-dual}),
  evaluation-locus factorization comparison
  (Theorem~\ref{thm:factorization-dk-eval}),
  DK-2/3 on the evaluation-generated core at all simple types
  (Corollary~\ref{cor:dk23-all-types}),
  and finite-stage packet reductions.
\item \emph{Conjectural but well-posed.}
  The filtered H-level dg target
  $\mathcal{W}^{\mathrm{ht}}$, RTT-adapted finite-quotient
  package, coefficientwise RTT completion comparison,
  and compact-generator packet
  (Conjecture~\ref{conj:master-infinite-generator}).
\item \emph{Downstream physics.}
  The dg-shifted Yangian realization, full DK-4/5 bridge,
  and module-category enhancement
  (Chapter~\ref{ch:bv-brst}).
\end{enumerate}
Layer~(A) is the proved DK core.  Layer~(B) is the live
algebraic frontier.  Layer~(C) is downstream of~(B) and of
MC5.
\end{remark}

\begin{remark}[DK as genus-\texorpdfstring{$0$}{0} \texorpdfstring{$\Eone$}{E1}-factorization theorem]
\label{rem:dk-e1-factorization}
\index{Drinfeld--Kohno!as E1 factorization theorem@as $\Eone$-factorization theorem}
The correct ontological ladder for the DK comparison is not
``$\Eone \to \Etwo$'' as if $\Etwo$ were ``more commutative
Yangian.''  Rather:
\begin{enumerate}[label=\textup{(\arabic*)}]
\item \emph{$\Eone$-chiral Yangian}: ordered fusion, $R$-matrix,
  DK monodromy.  This is Layers~(A)--(B) above.
\item \emph{Associator/GT layer}: the coherence upgrade problem
  from $\Eone$ to $\Etwo$ requires a Drinfeld associator
  (Remark~\ref{rem:e1-e2-obstruction}).
\item \emph{Modular layer}: genus and periods deform the entire
  $\Eone$-factorization package.  This is the content of modular
  homotopy theory (Definition~\ref{def:modular-homotopy-theory-intro}).
\end{enumerate}
DK compares geometric braid monodromy (from KZ/configuration
space) with algebraic braid data (from $R$-matrix/quantum group).
Both are realizations of the same $\Eone$-factorization transport
on ordered configurations.  DK is the genus-$0$ face; modular
homotopy theory asks what happens when the curve acquires genuine
moduli.
\end{remark}

\subsection{The Drinfeld--Kohno square for affine algebras}

\begin{theorem}[Chain-level derived Drinfeld--Kohno for affine algebras;
\ClaimStatusProvedHere]\label{thm:derived-dk-affine}
\index{Drinfeld--Kohno!derived!affine algebras}
Let $k$ be a non-negative integer,
$q = e^{\pi i/(k + h^\vee)}$, and $k' = -k - 2h^\vee$
\textup{(}so $q' = e^{\pi i/(k' + h^\vee)} = q^{-1}$\textup{)}.
The module Koszul duality functor
$\Phi \colon D^b(\mathcal{O}_k^{\mathrm{int}}(\widehat{\mathfrak{g}}))
\to D^b(\mathcal{O}_{k'}(\widehat{\mathfrak{g}}))$
\textup{(}Theorem~\textup{\ref{thm:e1-module-koszul-duality})}
fits into a commutative square of braided monoidal functors:
\begin{equation}\label{eq:dk-square-affine}
\begin{tikzcd}
\mathcal{O}_k^{\mathrm{int}}(\widehat{\mathfrak{g}})
  \ar[r, "\Phi", "\sim"']
  \ar[d, "\Phi_{\mathrm{KL}}"', "\sim"]
& \mathcal{O}_{k'}(\widehat{\mathfrak{g}})
  \ar[d, "\Phi_{\mathrm{KL}}", "\sim"']
\\
\mathcal{C}(U_q(\mathfrak{g}))
  \ar[r, "q \mapsto q^{-1}"', "\sim"]
& \mathcal{C}(U_{q^{-1}}(\mathfrak{g}))
\end{tikzcd}
\end{equation}
where the vertical arrows are the Kazhdan--Lusztig equivalences
\textup{(}Theorem~\textup{\ref{thm:kazhdan-lusztig-equivalence})},
the top arrow is the module Koszul duality functor with braiding
reversal
\textup{(}Theorem~\textup{\ref{thm:monoidal-module-koszul})}, and
the bottom arrow is the $R$-matrix inversion
$R_q \mapsto R_{q^{-1}} = R_q^{-1}$.  All four functors are
equivalences of braided monoidal categories.
\end{theorem}

\begin{proof}
We verify commutativity of the diagram on objects,
morphisms, tensor products, and braiding.

\emph{Step~1: Objects.}
The top arrow $\Phi$ sends the integrable module $L(\Lambda)$
at level~$k$ to the Koszul dual module at level $k' = -k - 2h^\vee$
(Theorem~\ref{thm:universal-kac-moody-koszul}).  The left vertical sends
$L(\Lambda)$ to the tilting module $T_q(\Lambda)$
(Theorem~\ref{thm:kazhdan-lusztig-equivalence}).  Traversing the
diagram in both directions: $\Phi_{\mathrm{KL}} \circ \Phi$
sends $L(\Lambda)$ to $T_{q^{-1}}(\Lambda)$ (since $q' = q^{-1}$),
which is $\Phi_{\mathrm{KL}}(L(\Lambda))$ in the
$q^{-1}$-category.  This equals the image under
$(q \mapsto q^{-1}) \circ \Phi_{\mathrm{KL}}$, since the
$q \mapsto q^{-1}$ functor sends $T_q(\Lambda)$ to
$T_{q^{-1}}(\Lambda)$ (the labeling by dominant weights $\Lambda$
is independent of the sign of~$q$).

\emph{Step~2: Braiding.}
The braiding on $\mathcal{O}_k^{\mathrm{int}}$ is the
monodromy of the KZ connection on conformal blocks.  By the
classical Kohno--Drinfeld theorem \cite{Kohno87, Drinfeld90},
$\Phi_{\mathrm{KL}}$ sends this monodromy to the quasi-$R$-matrix
$\mathcal{R}_q \in U_q(\mathfrak{g})^{\widehat{\otimes}\,2}$.
The top arrow $\Phi$ reverses the braiding:
$\sigma \mapsto \sigma^{-1}$
(Theorem~\ref{thm:monoidal-module-koszul}, step~3).
On the quantum group side, this corresponds to
$\mathcal{R}_q \mapsto \mathcal{R}_q^{-1} = \mathcal{R}_{q^{-1}}$,
which is precisely the bottom arrow.

\emph{Step~3: Tensor structure.}
The top arrow preserves the monoidal structure up to braiding reversal
(Theorem~\ref{thm:monoidal-module-koszul}, step~2): the bar complex
of the fusion product $M \boxtimes N$ decomposes via the Alexander--Whitney
map into the cotensor product of the individual bar complexes.
The KL equivalence identifies the fusion product with the quantum group
tensor product \cite{KL93}, and the $q \mapsto q^{-1}$ functor
preserves the tensor product structure (the underlying fusion rules
depend only on $\mathfrak{g}$, not on the sign of~$q$).
\end{proof}

\begin{remark}[The DK square as geometry]\label{rem:dk-square-geometry}
The four arrows of the DK square~\eqref{eq:dk-square-affine} have
distinct geometric origins:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ll}
\textbf{Top}: & Verdier duality on $\overline{C}_n(\bP^1)$
  reverses collision cycles \\
\textbf{Left/Right}: & KZ monodromy $=$ quasi-$R$-matrix
  (analytic continuation) \\
\textbf{Bottom}: & $R_q \mapsto R_{q^{-1}} = R_q^{-1}$
  (Hopf algebra involution)
\end{tabular}
\end{center}
The commutativity of the square is the statement that
bar-cobar duality \emph{geometrically implements} the quantum
group involution: the algebraic operation $q \mapsto q^{-1}$
is realized by orientation reversal on configuration spaces.
\end{remark}

\subsection{Chain-level derived Drinfeld--Kohno for Yangians}

\begin{theorem}[Derived Drinfeld--Kohno on the evaluation-generated subcategory;
\ClaimStatusProvedHere]\label{thm:derived-dk-yangian}
\index{Drinfeld--Kohno!derived!Yangian}
%
\textup{[Category: the evaluation-generated subcategory of
$\operatorname{Rep}_{\mathrm{fd}}(U_q(\mathfrak{g}))$,
not the semisimplified tilting category
$\mathcal{C}(U_q(\mathfrak{g}))$ of
Theorem~\textup{\ref{thm:derived-dk-affine}}.
Extension to all of
$\operatorname{Rep}_{\mathrm{fd}}$ in type~$A$
requires the thick generation argument of
Theorem~\textup{\ref{thm:dk-fd-typeA}}.]}
%
For $\mathfrak{g} = \mathfrak{sl}_N$, let
$\operatorname{Rep}_{\mathrm{fd}}^{\mathrm{eval}}(Y_\hbar(\mathfrak{g}))
\subset \operatorname{Rep}_{\mathrm{fd}}(Y_\hbar(\mathfrak{g}))$
denote the full subcategory generated by evaluation modules.
The $\Eone$-chiral Koszul duality functor restricts to
\[
\Phi \colon D^b(\operatorname{Rep}_{\mathrm{fd}}^{\mathrm{eval}}(Y_\hbar(\mathfrak{g})))
\;\to\;
D^b(\operatorname{Rep}_{\mathrm{fd}}^{\mathrm{eval}}(Y_{-\hbar}(\mathfrak{g})))
\]

and fits into the same square as the Kazhdan equivalence
\[
\operatorname{Rep}_{\mathrm{fd}}(Y_\hbar(\mathfrak{g}))
\simeq
\operatorname{Rep}_{\mathrm{fd}}(U_q(\mathfrak{g}))
\big|_{q = e^\hbar}
\]
\cite{Drinfeld85}.

The claim is that this square commutes on evaluation modules:
\begin{equation}\label{eq:dk-square-yangian}
\begin{tikzcd}
D^b(\operatorname{Rep}_{\mathrm{fd}}^{\mathrm{eval}}(Y_\hbar))
  \ar[r, "\Phi"]
  \ar[d, "\Phi_K"']
& D^b(\operatorname{Rep}_{\mathrm{fd}}^{\mathrm{eval}}(Y_{-\hbar}))
  \ar[d, "\Phi_K"]
\\
D^b(\operatorname{Rep}_{\mathrm{fd}}(U_q))
  \ar[r, "q \mapsto q^{-1}"']
& D^b(\operatorname{Rep}_{\mathrm{fd}}(U_{q^{-1}}))
\end{tikzcd}
\end{equation}

The top arrow reverses the braiding:
$\sigma_R \mapsto \sigma_{R^{-1}}$
\textup{(}Proposition~\textup{\ref{prop:yangian-module-koszul}(iii))}.

Under the Kazhdan identification $\Phi_K$, this becomes the
$q \mapsto q^{-1}$ involution on quantum group representations.

In particular, the $\Eone$-chiral bar-cobar duality of the Yangian
provides a chain-level derived shadow of the Drinfeld--Kohno
correspondence.  The extension to all finite-dimensional
representations in type~$A$ is Theorem~\textup{\ref{thm:dk-fd-typeA}},
which uses an explicit thick generation argument.
\end{theorem}

\begin{proof}
\emph{Step~1: The Kazhdan equivalence.}
The Kazhdan functor~\cite{Drinfeld85}
$\Phi_K \colon \operatorname{Rep}_{\mathrm{fd}}(Y_\hbar(\mathfrak{g}))
\xrightarrow{\sim}
\operatorname{Rep}_{\mathrm{fd}}(U_q(\mathfrak{g}))$
at $q = e^\hbar$ is a monoidal equivalence that sends
the $R$-matrix $R_Y(u) = 1 - \hbar P/u$ of the Yangian
to the trigonometric $R$-matrix $R_q$ of the quantum group
via the exponential map
$R_Y(u) \mapsto R_q(e^u)$.  On evaluation modules,
$\Phi_K(V(a)_\hbar) = V_q(e^a)$, where $V_q(z)$ denotes
the evaluation module of
$U_q(\widehat{\mathfrak{g}})$ at spectral parameter
$z = e^a$.

\smallskip\noindent\emph{Step~2: Commutativity on evaluations.}
The top arrow~$\Phi$ sends $V(a)_\hbar$ to
$V(-a)_{-\hbar}$
(Proposition~\ref{prop:yangian-module-koszul}(i)).

Applying~$\Phi_K$ to the right column yields
$V(-a)_{-\hbar}$ $\mapsto$ $V_{q^{-1}}(e^{-a})$.
Applying~$\Phi_K$ first (left column) followed by
$q \mapsto q^{-1}$ gives
\[
V(a)_\hbar \,\mapsto\, V_q(e^a) \,\mapsto\, V_{q^{-1}}(e^a).
\]
These agree when
$V_{q^{-1}}(e^{-a}) \cong V_{q^{-1}}(e^a)$
as abstract $U_{q^{-1}}(\mathfrak{g})$-modules, which
holds because evaluation modules of a quantum loop
algebra at the same highest weight are isomorphic as
$U_{q^{-1}}(\mathfrak{g})$-modules
(the evaluation point only affects the loop algebra
action, not the underlying
$U_{q^{-1}}(\mathfrak{g})$-structure).

\emph{Step~3: Braiding.}
On the Yangian side, the braiding is
$\sigma_Y = P \circ R_Y(u)$, and $\Phi$ sends it to
$\sigma_Y^{-1} = P \circ R_Y^{-1}(u)$
(Proposition~\ref{prop:yangian-module-koszul}(iii)).
The Kazhdan functor identifies $R_Y(u)$ with $R_q(e^u)$,
so $R_Y^{-1}(u) \mapsto R_q^{-1}(e^u) = R_{q^{-1}}(e^u)$.
This is precisely the braiding on the $q^{-1}$ side.

\emph{Step~4: Ext exchange.}
Corollary~\ref{cor:yangian-ext-exchange} gives
\[
\operatorname{Ext}^n_{Y_\hbar}(V(a), W(b))
\cong \operatorname{Ext}^n_{Y_{-\hbar}}(V(-a), W(-b)).
\]
The transport takes place via the Kazhdan equivalence in the full
abelian category of finite-dimensional $U_q(\mathfrak{g})$-modules.
Via $\Phi_K$, this becomes
\[
\operatorname{Ext}^n_{U_q}(V_q(e^a), W_q(e^b))
\cong \operatorname{Ext}^n_{U_{q^{-1}}}(V_{q^{-1}}(e^{-a}),
W_{q^{-1}}(e^{-b})),
\]
the derived enhancement of the classical DK identification.
\end{proof}

\subsection{The factorization-level statement}

\begin{definition}[\texorpdfstring{$\Eone$}{E1}-factorization category]
\label{def:e1-factorization-category}
\index{E1-factorization category@$\Eone$-factorization category|textbf}
For an $\Eone$-chiral algebra $\cA$ on a curve $X$, the
\emph{$\Eone$-factorization category}
$\operatorname{Fact}_{\Eone}(\cA)$ consists of:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Objects:} $\cA$-modules on ordered configuration spaces
  $C_n^{\mathrm{ord}}(X) = \{(z_1, \ldots, z_n) : z_i \neq z_j\}$.
\item \emph{Factorization structure:} for disjoint intervals
  $I_1, \ldots, I_k \subset X$, isomorphisms
  $\cA\text{-mod}(C_{n_1}^{\mathrm{ord}}(I_1) \times \cdots
  \times C_{n_k}^{\mathrm{ord}}(I_k))
  \xrightarrow{\sim}
  \cA\text{-mod}(C_n^{\mathrm{ord}}(\bigcup I_j))$.
\item \emph{Braiding:} the braid group $B_n$ acts on
  $C_n^{\mathrm{ord}}(X)$ by monodromy around the diagonals.
  The $R$-matrix $R_\cA$ encodes this monodromy.
\item \emph{Monoidal structure:} the fusion product
  $\boxtimes_\cA$ on modules, given by colliding
  points along ordered intervals.
\end{enumerate}
\end{definition}

\begin{theorem}[Factorization DK on evaluation locus;
\ClaimStatusProvedHere]\label{thm:factorization-dk-eval}
\index{Drinfeld--Kohno!derived!factorization}
Restrict to the full subcategory
$\operatorname{Fact}_{\Eone}^{\mathrm{eval}}(Y(\mathfrak{sl}_N))$
generated by tensor products of evaluation modules.  The
$\Eone$-chiral bar-cobar functor induces an equivalence of
$\Eone$-factorization categories:
\begin{equation}\label{eq:factorization-dk-eval}
\Phi \colon
\operatorname{Fact}_{\Eone}^{\mathrm{eval}}(Y_\hbar(\mathfrak{sl}_N))
\;\xrightarrow{\;\sim\;}\;
\operatorname{Fact}_{\Eone}^{\mathrm{eval}}
  (Y_{-\hbar}(\mathfrak{sl}_N))^{\mathrm{op}}
\end{equation}
with the following properties:
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{On objects:} $V(a_1) \otimes \cdots \otimes V(a_n)
  \;\mapsto\; V(-a_1) \otimes \cdots \otimes V(-a_n)$
  with $\hbar \mapsto -\hbar$.
\item \emph{On braiding:}
  $R(u; \hbar) \;\mapsto\; R^{-1}(u; \hbar) = R(u; -\hbar)$.
\item \emph{On factorization:} the factorization isomorphisms
  are preserved, with the $\Eone$-ordering reversed
  \textup{(}reflecting the ``op'' on the target\textup{)}.
\end{enumerate}
\end{theorem}

\begin{proof}
Part~(i) is Proposition~\ref{prop:yangian-module-koszul}(i)
applied to each tensor factor.  Part~(ii) is
Proposition~\ref{prop:yangian-module-koszul}(iii).  For
part~(iii): the factorization isomorphisms on the source are
encoded by the bar complex propagator $\eta_{ij} = d\log(z_i - z_j)$
on $\overline{C}_n^{\mathrm{ord}}(X)$.  The Verdier involution
(Theorem~\ref{thm:bar-cobar-verdier}) acts on the
compactified configuration space by reversing the orientation of
collision cycles, which reverses the ordering of the
$\Eone$-intervals.  The bar-cobar quasi-isomorphism
(Corollary~\ref{cor:yangian-bar-cobar}) ensures this
factorization structure is inherited by the dual, producing
the ``op'' monoidal structure on the target.
\end{proof}

\subsection{The staged ladder beyond the evaluation locus}

The evaluation-module results above establish the derived
Drinfeld--Kohno correspondence at the chain level and on the
evaluation locus.  The remaining work is not one undifferentiated
conjectural jump: it is the staged passage from DK-2 through DK-5 of
Remark~\ref{rem:yangian-status}.  First one enlarges the theorematic
evaluation-generated core to the natural
ordinary-derived/completed/coderived ambient; only after that
enlargement is fixed does the standard-tower MC4 comparison begin.
The first H-level bridge targets all modules:

\begin{conjecture}[Factorization-categorical DK/KL bridge (DK-3);
\ClaimStatusConjectured]\label{conj:full-derived-dk}
\index{Drinfeld--Kohno!derived!full conjecture}
The equivalence of
Theorem~\textup{\ref{thm:factorization-dk-eval}} extends to the
full $\Eone$-factorization category:
\begin{equation}\label{eq:full-dk}
\operatorname{Fact}_{\Eone}(\mathcal{Y}(\mathfrak{g}))
\;\simeq\;
\operatorname{Fact}_{\Eone}(U_q(\mathfrak{g}))^{\mathrm{op}},
\end{equation}
where $\mathcal{Y}(\mathfrak{g})$ is the Yangian
$\Eone$-chiral algebra and $U_q(\mathfrak{g})$ is the quantum
group, viewed as an $\Eone$-factorization algebra via the
construction of Latyntsev~\cite{Latyntsev23}.
This is the factorization-level Kazhdan bridge beyond the evaluation
subcategories; it separates the ordered Yangian factorization problem
from the later dg-shifted comparison of
Conjecture~\ref{conj:full-dk-bridge}.
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\end{conjecture}

\begin{proposition}[DK-3 reduction to evaluation-generated
factorization cores; \ClaimStatusProvedHere]
\label{prop:yangian-dk3-generated-core}
Let
\[
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\mathcal{Y}(\mathfrak{g}))
\subset \operatorname{Fact}_{\Eone}(\mathcal{Y}(\mathfrak{g})),
\qquad
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(U_q(\mathfrak{g}))
\subset \operatorname{Fact}_{\Eone}(U_q(\mathfrak{g}))
\]
be the smallest full stable idempotent-complete braided monoidal
subcategories containing all ordered tensor products of evaluation
objects.  Assume there exist exact braided monoidal functors
\[
KZ_{\mathrm{fact}}^{\mathrm{gen}}\colon
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\mathcal{Y}(\mathfrak{g}))
\to
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(U_q(\mathfrak{g}))^{\mathrm{op}},
\]
\[
LZ_{\mathrm{fact}}^{\mathrm{gen}}\colon
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(U_q(\mathfrak{g}))^{\mathrm{op}}
\to
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\mathcal{Y}(\mathfrak{g})),
\]
whose restrictions to the evaluation generators recover the
evaluation-locus comparison of
Theorem~\ref{thm:factorization-dk-eval} after transport to the
quantum-group evaluation side, and such that both composites are
isomorphic to the identity on those generators.  Then the two functors
are quasi-inverse braided monoidal equivalences on the generated cores.
If, in addition,
\[
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\mathcal{Y}(\mathfrak{g}))
=
\operatorname{Fact}_{\Eone}(\mathcal{Y}(\mathfrak{g})),
\qquad
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(U_q(\mathfrak{g}))
=
\operatorname{Fact}_{\Eone}(U_q(\mathfrak{g})),
\]
then Conjecture~\ref{conj:full-derived-dk} holds.
\end{proposition}

\begin{proof}
The generated cores are obtained from the evaluation generators by
finite iterates of shifts, cones, direct summands, and ordered tensor
products.  Exact braided monoidal functors preserve each of these
operations.  Therefore any natural transformation between exact
braided monoidal functors that is an isomorphism on the evaluation
generators remains an isomorphism on the full generated cores.  Applying
this to the two composites shows that they are naturally isomorphic to
the identity on the generated cores, hence the two functors are
quasi-inverse equivalences there.  The final sentence is immediate.
\end{proof}

\begin{remark}[Exact extra inputs for DK-2/DK-3]
\label{rem:yangian-dk23-inputs}
Propositions~\ref{prop:yangian-dk2-thick-generation}
and~\ref{prop:yangian-dk3-generated-core} make the remaining Yangian
DK inputs exact.  After the evaluation-locus theorem, the live extra
packets are:
\begin{enumerate}[label=\textup{(\roman*)}]
\item preservation or replacement resolution theory on the completed
  Yangian categories~$\mathcal{O}$;
\item thick generation of those derived categories by evaluation
  modules --- proved in type~A
  (Proposition~\ref{prop:dk2-thick-generation-typeA});
\item construction of the ordered factorization Kazhdan transport on
  the evaluation-generated factorization core --- a natural candidate
  is identified (Proposition~\ref{prop:bar-cobar-kazhdan-candidate});
  what remains is strict factorization-monoidal enhancement
  (Remark~\ref{rem:dk3-remaining-after-barcobar}); and
\item a reconstruction argument, Barr--Beck style or equivalent,
  producing the quasi-inverse pair on that core.
\end{enumerate}
For finite-dimensional representations in type~$A$,
items~(ii)--(iv) are resolved by
Theorem~\ref{thm:dk-fd-typeA}: thick generation
(Proposition~\ref{prop:dk2-thick-generation-typeA}) eliminates~(ii),
and the monoidal thick extension
(Lemma~\ref{lem:monoidal-thick-extension}) resolves~(iii)--(iv)
by extending the evaluation-level data to the thick closure.
The live extra packets are therefore:
(i)~preservation for category~$\mathcal{O}$ and
thick generation beyond $\operatorname{Rep}_{\mathrm{fd}}$.
None of these is a new residue computation on evaluation modules.  The
residue/RTT identities begin only at the downstream DK-4/MC4 boundary.
\end{remark}

\begin{remark}[DK ladder: what is proved and what remains]
\label{rem:dk-proved-vs-remains}
\textbf{DK-0/1}: chain-level braided bar-cobar (Theorems~\ref{thm:e1-chiral-koszul-duality}--\ref{thm:derived-dk-yangian}) and evaluation-locus factorization DK (Theorem~\ref{thm:factorization-dk-eval}) --- proved.  \textbf{DK-2/3}: evaluation-generated core, all simple types --- proved by thick generation in type~$A$ (Theorem~\ref{thm:dk-fd-typeA}) and sectorwise convergence for all types (Corollary~\ref{cor:dk23-all-types}); category-$\mathcal{O}$ extension conjectural (Conjecture~\ref{conj:full-derived-dk}, reduces to thick generation by Corollary~\ref{cor:dk-partial-conj}).  \textbf{DK-4/5}: conjectural (Conjecture~\ref{conj:full-dk-bridge}; see Remark~\ref{rem:yangian-dk23-inputs} for exact inputs).  Contributing to Conjecture~\ref{conj:master-dk-kl}.
\end{remark}

\subsection{$\infty$-categorical factorization Koszul duality}
\label{sec:infty-cat-factorization-kd}
\index{Koszul duality!factorization!infinity-categorical@$\infty$-categorical|textbf}

The DK ladder as formulated in
Remark~\ref{rem:dk-proved-vs-remains} decomposes the factorization
Koszul duality problem into five stages, with DK-0/1/2/3 proved on the evaluation-generated
core at all simple types and DK-4/5 conjectural.  From first principles, the
entire ladder is a single $\infty$-categorical statement: Koszul
duality for $\Eone$-algebras in the symmetric monoidal stable
$\infty$-category of factorization coalgebras on~$\operatorname{Ran}(X)$.
We make this precise and show that DK-2/3 extends to the
evaluation-generated core at all types via
sectorwise convergence, bypassing thick generation, and that DK-4/5
reduces to a formal deformation theory comparison within the same
framework.

\subsubsection*{Sectorwise convergence and DK-2/3 for the evaluation-generated core at all types}

\begin{theorem}[Sectorwise spectral convergence;
\ClaimStatusProvedHere]
\label{thm:sectorwise-spectral-convergence}
\index{spectral sequence!sectorwise convergence}
\index{bar complex!sectorwise convergence}
For any simple~$\fg$, the loop spectral sequence of
Proposition~\ref{prop:yangian-bar-loop-weight} stabilizes at each
tridegree: for each $\gamma \in Q(\fg)$ and each $(p,q)$, there
exists~$r_0 = r_0(p,q,\gamma) < \infty$ such that
\[
E_\infty^{p,q}(\barB_\gamma^{\mathrm{fact}})
\;=\; E_{r_0}^{p,q}(\barB_\gamma^{\mathrm{fact}}).
\]
Moreover:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $\dim {E_\infty}^{p,q}_\gamma \le \dim {E_1}^{p,q}_\gamma$ at each
  tridegree, so the $E_\infty$ page inherits the sub-exponential
  growth bound of
  Proposition~\ref{prop:lqt-e1-subexponential-growth};
\item the $E_\infty$ page carries a well-defined factorization
  coalgebra structure, compatible with the $Q(\fg)$-grading
  and the factorization isomorphisms on
  $\operatorname{Ran}(X)$.
\end{enumerate}
\end{theorem}

\begin{proof}
Each ${E_0}^{p,q}_\gamma$ is finite-dimensional
(Proposition~\ref{prop:yangian-bar-loop-weight}(c)).  Since
${E_{r+1}}^{p,q}$ is a subquotient of ${E_r}^{p,q}$, the sequence
$\dim {E_r}^{p,q}_\gamma$ is non-increasing and non-negative, hence
eventually constant.  This gives the first claim and~(a).

For~(b): by Proposition~\ref{prop:yangian-bar-loop-weight}(a,b),
the factorization coalgebra structure on $\barB^{\mathrm{fact}}$
preserves the $Q(\fg)$-grading and is compatible with the loop
filtration~$F^\bullet$; it therefore descends to each page~$E_r$
and to~$E_\infty$.
\end{proof}

The sectorwise convergence is the key finiteness input for extending
the bar-cobar equivalence from the diagonal to the full
$\operatorname{Ran}$ space.  The argument generalizes the
lattice bypass of DK-$1\frac{1}{2}$
(Theorem~\ref{thm:lattice:factorization-koszul}): in the lattice
case, $E_1 = 0$ (Heisenberg acyclicity) gave immediate degeneration;
here the $E_\infty$ page is nontrivial but finite-dimensional, which
suffices for the factorization descent.

\begin{theorem}[\texorpdfstring{$\infty$}{infinity}-categorical factorization Koszul duality
via sectorwise convergence; \ClaimStatusProvedHere]
\label{thm:h-level-factorization-kd}
\index{Koszul duality!factorization!sectorwise|textbf}
\index{sectorwise finiteness!factorization Koszul duality}
Let~$\cA$ be an $\Eone$-chiral algebra on a smooth curve~$X$
satisfying:
\begin{enumerate}[label=\textup{(H\arabic*)}]
\item\label{h1:koszulness} \emph{$\Eone$-Koszulness}: the cobar-bar
  counit
  $\Omega(\barB(\cA)) \to \cA$ is a quasi-isomorphism
  \textup{(}Theorem~B on the Koszul locus\textup{)};
\item\label{h2:sectorwise} \emph{Sectorwise finiteness}: the
  factorization bar complex $\barB^{\mathrm{fact}}(\cA)$ admits a
  $\Gamma$-grading \textup{(}for a finitely generated abelian
  group~$\Gamma$\textup{)} and a descending
  filtration~$F^\bullet$ compatible with the grading, such that
  $\operatorname{gr}^p \barB_\gamma$ is finite-dimensional
  over each $\operatorname{Ran}$-stratum;
\item\label{h3:convergence} \emph{Spectral convergence}: the
  associated spectral sequence stabilizes at each tridegree
  \textup{(}automatic by
  Theorem~\textup{\ref{thm:sectorwise-spectral-convergence}}
  when~\ref{h2:sectorwise} holds\textup{)}.
\end{enumerate}
Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The factorization bar-cobar counit
  \[
  \varepsilon^{\mathrm{fact}}\colon
  \Omega^{\mathrm{fact}}(\barB^{\mathrm{fact}}(\cA)) \to \cA
  \]
  is a quasi-isomorphism of factorization algebras on
  $\operatorname{Ran}(X)$.
\item The factorization Verdier intertwining
  $\mathbb{D}_{\mathrm{Ran}}\,
  \barB^{\mathrm{fact}}(\cA)
  \simeq \barB^{\mathrm{fact}}(\cA^!)$
  holds at the factorization level.
\item The module bar functor
  \[
  \barB_{\mathrm{mod}}^{\mathrm{fact}}\colon
  \operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\cA)
  \to
  \operatorname{CoFact}_{\Eone}^{\mathrm{gen}}
    (\cA^{!,c})^{\mathrm{op}}
  \]
  is an equivalence of stable $\infty$-categories on the
  evaluation-generated cores, with braiding reversal
  $R \mapsto R^{-1}$.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Part~(i): factorization bar-cobar.}
On the diagonal stratum $\operatorname{Ran}_1(X) \cong X$, the
factorization counit $\varepsilon^{\mathrm{fact}}$ restricts to
the ordinary cobar-bar counit
$\varepsilon\colon \Omega(\barB(\cA)) \to \cA$,
which is a quasi-isomorphism by hypothesis~\ref{h1:koszulness}
(Theorem~B).

For $n \ge 2$ and disjoint opens
$U_1, \ldots, U_k \subset X$, the factorization isomorphisms
decompose both source and target:
\begin{align*}
\Omega^{\mathrm{fact}}(\barB^{\mathrm{fact}}(\cA))
  (U_1 \sqcup \cdots \sqcup U_k)
&\cong \bigotimes_{j=1}^k
  \Omega^{\mathrm{fact}}(\barB^{\mathrm{fact}}(\cA))(U_j), \\
\cA(U_1 \sqcup \cdots \sqcup U_k)
&\cong \bigotimes_{j=1}^k \cA(U_j).
\end{align*}
The counit decomposes as $\varepsilon^{\mathrm{fact}}
= \varepsilon|_{U_1} \otimes \cdots \otimes \varepsilon|_{U_k}$,
and each factor $\varepsilon|_{U_j}$ is a quasi-isomorphism
by hypothesis~\ref{h1:koszulness} on the single-point stratum;
the K\"unneth formula for derived tensor products of chain
complexes over a field preserves quasi-isomorphisms, so the
tensor product is a quasi-isomorphism.

On arbitrary opens (including overlapping configurations), the
factorization algebra is determined by descent: a factorization
algebra on~$\operatorname{Ran}(X)$ is a cosheaf for the
factorization topology, whose basis consists of products of disjoint
opens.  Sectorwise finiteness~\ref{h2:sectorwise} guarantees that
$\barB^{\mathrm{fact}}(\cA)$ is a genuine factorization coalgebra
on~$\operatorname{Ran}(X)$ (not merely a formal pro-object), so
the cosheaf condition applies.  A map of factorization cosheaves
that is a quasi-isomorphism on every basis open is a global
quasi-isomorphism, giving~(i).

\emph{Part~(ii): Verdier intertwining.}
The Verdier intertwining on~$\operatorname{Ran}_1$ is
Theorem~A\textsubscript{2}
(Theorem~\ref{thm:bar-cobar-verdier}).
For disjoint opens
$U_1 \sqcup \cdots \sqcup U_k$, Verdier duality distributes as
$\mathbb{D}_{\mathrm{Ran}}
\simeq \mathbb{D}_{U_1} \boxtimes \cdots \boxtimes \mathbb{D}_{U_k}$,
so the factorization bar intertwining decomposes into a tensor
product of the $\operatorname{Ran}_1$ intertwining on each factor.
The same cosheaf descent as part~(i) extends from disjoint to
arbitrary opens.

\emph{Part~(iii): module equivalence.}
On evaluation objects, the module bar functor is an equivalence by
DK-1 (Theorem~\ref{thm:factorization-dk-eval}).  The
evaluation-generated core
$\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\cA)$ is the
smallest full stable idempotent-complete braided monoidal subcategory
containing all evaluation objects.  Since the module bar functor
is exact and braided monoidal with reversal
(Theorem~\ref{thm:monoidal-module-koszul}), it preserves shifts,
cones, direct summands, and ordered tensor products.  Therefore, by
Proposition~\ref{prop:yangian-dk3-generated-core}, any natural
isomorphism between the identity and
$\Omega_{\mathrm{mod}} \circ \barB_{\mathrm{mod}}$ that holds on
evaluation generators extends to the full generated core.

The braiding reversal $R \mapsto R^{-1}$ is
Proposition~\ref{prop:yangian-module-koszul}(iii), extended to the
generated core by functoriality.
\end{proof}

\begin{remark}[Scope of ``unconditional'']
\label{rem:dk23-unconditional-scope}
\index{Drinfeld--Kohno!unconditional!scope}
The following corollary is ``unconditional'' in the sense that it
does not require thick generation: the sectorwise convergence
argument works for all simple types without identifying the
generated core with $D^b(\operatorname{Rep}_{\mathrm{fd}})$.
It does, however, depend on the classical Koszulness of the RTT
Yangian (Proposition~\ref{prop:yangian-koszul}), whose proof
uses Molev's PBW theorem \cite{molev-yangians} as external input.
\end{remark}

\begin{corollary}[DK-2/3 for all simple types via sectorwise
convergence; \ClaimStatusProvedHere]
\label{cor:dk23-all-types}
\index{Drinfeld--Kohno!derived!all types}
\index{sectorwise finiteness!DK for all types}
For $\fg$ any simple Lie algebra, the factorization bar-cobar
functor induces an equivalence on the evaluation-generated cores:
\begin{equation}\label{eq:dk23-all-types}
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}
  (Y_\hbar(\fg))
\;\xrightarrow{\;\sim\;}\;
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}
  (Y_{-\hbar}(\fg))^{\mathrm{op}},
\end{equation}
extending the evaluation-locus DK equivalence
\textup{(}Theorem~\textup{\ref{thm:factorization-dk-eval}}\textup{)}
to the full generated core at all types, without any
thick-generation argument.
\end{corollary}

\begin{proof}
Apply Theorem~\ref{thm:h-level-factorization-kd} to
$\cA = \mathcal{Y}(\fg)$.
Hypothesis~\ref{h1:koszulness} is
Corollary~\ref{cor:yangian-bar-cobar}: the RTT Yangian is
quadratic, pro-nilpotent, and Koszul
(Proposition~\ref{prop:yangian-koszul}), so
Theorem~\ref{thm:e1-chiral-koszul-duality} gives the
$\Eone$-chiral bar-cobar quasi-isomorphism for every
simple~$\fg$.
Hypothesis~\ref{h2:sectorwise} is
Proposition~\ref{prop:yangian-bar-loop-weight}: the $Q(\fg)$-grading
and loop filtration give the required sectorwise-finite bifiltration
for every simple~$\fg$.
Hypothesis~\ref{h3:convergence} follows from
Theorem~\ref{thm:sectorwise-spectral-convergence}.
Conclusion~(iii) gives~\eqref{eq:dk23-all-types}.
\end{proof}

\begin{remark}[H/M/S semantic levels for DK-2/3]
\label{rem:dk23-hms}
\index{Drinfeld--Kohno!H/M/S levels}
\emph{Step~A} (H-level):
Theorem~\ref{thm:h-level-factorization-kd} asserts an
equivalence of stable $\infty$-categories
$\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\cA)
\simeq
\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\cA^!)^{\mathrm{op}}$
on the evaluation-generated cores, with braiding reversal
$R \mapsto R^{-1}$.  This is the theorem.

\emph{Step~B} (M-level):
The proof is a dg chain-level argument: sectorwise convergence
of the bar spectral sequence on each
$\operatorname{Ran}$-stratum, extended to the full factorization
cosheaf by descent.  Concretely, the module bar functor is exact
and braided monoidal
(Theorem~\ref{thm:monoidal-module-koszul}), and the
quasi-isomorphism on evaluation generators extends to the
generated core by functoriality
(Proposition~\ref{prop:yangian-dk3-generated-core}).

\emph{Reduction B$\to$A} (M-level $\to$ H-level):
The dg descent implies the $\infty$-categorical equivalence: a
map of factorization cosheaves that is a quasi-isomorphism on
every basis open is a global quasi-isomorphism in the
$\infty$-categorical sense
(Lurie~\cite[Proposition~5.5.2.2]{HA}).  Thus the M-level
sectorwise quasi-isomorphisms determine the H-level equivalence
of stable $\infty$-categories.

\emph{Step~C} (S-level):
The shadow is the equality of graded dimensions
$\dim \operatorname{Ext}^i_{\cA}(V_\lambda, V_\mu)
= \dim \operatorname{Ext}^i_{\cA^!}(V_\lambda^!, V_\mu^!)$
across evaluation modules, together with the Kazhdan--Lusztig
multiplicity formula transported to the Koszul dual side.

\emph{Reduction B$\to$C} (M-level $\to$ S-level):
Taking cohomology of the M-level module bar complex
$\bar{B}_{\mathrm{mod}}(M)$ extracts the S-level Ext groups.
The sectorwise spectral sequence
(Theorem~\ref{thm:sectorwise-spectral-convergence}) converges
at each tridegree, so the M-level quasi-isomorphism on
evaluation generators yields isomorphisms of Ext groups.
\end{remark}

\begin{remark}[Two proofs in type~\texorpdfstring{$A$}{A}; scope comparison]
\label{rem:two-dk-proofs}
\index{Drinfeld--Kohno!two proofs}
For $\fg = \mathfrak{sl}_N$, there are now two independent proofs
of DK-2/3 on the evaluation-generated core:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Thick generation}
  \textup{(}Theorem~\ref{thm:dk-fd-typeA}\textup{)}: uses the
  Drinfeld polynomial classification to show that evaluation modules
  generate all finite-dimensional simples, then the composition-length
  argument of Lemma~\ref{lem:composition-thick-generation}.  This proof
  is representation-theoretic and specific to type~$A$.
\item \emph{Sectorwise convergence}
  \textup{(}Corollary~\ref{cor:dk23-all-types}\textup{)}: uses
  the root lattice grading and loop filtration to bypass thick
  generation entirely.  The proof is
  operadic/factorization-theoretic and works for all types.
\end{enumerate}
Proof~(b) is strictly more general (all types $A$--$G$),
but proof~(a) is more explicit: it identifies the generated core as
$D^b(\operatorname{Rep}_{\mathrm{fd}})$ via the Drinfeld
classification.  Proof~(b) identifies the generated core as the
thick closure of evaluation objects in the factorization category,
without naming the individual simples.
The two proofs agree on type~$A$: thick generation by evaluation
modules (Proposition~\ref{prop:dk2-thick-generation-typeA})
identifies the two generated cores.
\end{remark}

\begin{remark}[Interaction with the four-conjecture package]
\label{rem:h-level-vs-four-conjectures}
\index{MC3!four-conjecture package!interaction with H-level}
Theorem~\ref{thm:h-level-factorization-kd} and
Corollary~\ref{cor:dk23-all-types} resolve DK-2/3 for the
evaluation-generated core at all types.  The four conjectures of
Remark~\ref{rem:corrected-mc3-frontier}(b) ---
Baxter exact triangles
(Conjecture~\ref{conj:baxter-exact-triangles}),
shifted-prefundamental generation
(Conjecture~\ref{conj:shifted-prefundamental-generation}),
pro-Weyl recovery (Conjecture~\ref{conj:pro-weyl-recovery}), and
DK on compacts
(Conjecture~\ref{conj:dk-compacts-completion}) ---
concern the extension \emph{beyond} this core to
infinite-dimensional modules via a completed or coderived
enhancement.

The two programmes are complementary:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The sectorwise convergence theorem gives the strongest
  factorization equivalence on the natural domain
  (evaluation-generated core) at all types.
\item The four-conjecture package enlarges the domain to include
  prefundamental and asymptotic modules, requiring new input
  (Baxter TQ-lifts, pro-Weyl limits) beyond Koszul duality.
\item The formal moduli framework below provides the categorical
  home for both programmes: the evaluation-generated core is the
  compact part of the formal moduli problem, and the four-conjecture
  package extends to the completed/ind-completed part.
\end{enumerate}
\end{remark}

\subsubsection*{DK-4/5 as formal moduli Koszul duality}

The passage from DK-3 to DK-4/5 --- from the evaluation-generated
core to the full triple bridge --- gains conceptual clarity when
viewed through the lens of formal moduli problems for
$\Eone$-algebras.  The abstract framework exists
unconditionally (Lurie~\cite{LurieDAGX}); the content of DK-4 is
the identification of the tangent Lie algebra with the dg-shifted
Yangian, and DK-5 is the passage from Lie algebra modules to group
representations.

\begin{definition}[Factorization formal moduli problem]
\label{def:factorization-formal-moduli}
\index{formal moduli problem!factorization|textbf}
For an $\Eone$-chiral algebra~$\cA$ on~$X$, the
\emph{factorization formal moduli problem} is the functor
\[
\mathfrak{F}_{\cA}\colon
\mathrm{CAlg}^{\mathrm{aug}}_{k}
\to \mathcal{S},
\qquad
R \;\mapsto\;
\operatorname{Map}_{\mathrm{FAlg}_{\Eone}(X)}
  \bigl(\cA \otimes R,\, \cA \otimes R\bigr)^{\simeq}
\]
from augmented commutative $k$-algebras to spaces, where the mapping
space is taken in the $\infty$-category of
$\Eone$-factorization algebras on~$\operatorname{Ran}(X)$.

By Lurie's formal moduli theorem~\cite{LurieDAGX},
$\mathfrak{F}_{\cA}$ is controlled by a dg Lie algebra
$\mathfrak{g}_{\cA} := T_{*}\mathfrak{F}_{\cA}$,
the \emph{tangent Lie algebra} of the moduli problem.
The bar complex provides the chain-level model:
$\mathfrak{g}_{\cA} \simeq
\operatorname{Der}(\barB^{\mathrm{fact}}(\cA))$,
the derivations of the factorization bar coalgebra.
\end{definition}

\begin{proposition}[Canonical Yangian H-level dg target from factorization
formal moduli; \ClaimStatusProvedHere]
\label{prop:yangian-canonical-hlevel-target}
For every $\Eone$-chiral algebra $\cA$ on~$X$, the factorization
formal moduli problem $\mathfrak{F}_{\cA}$ of
Definition~\ref{def:factorization-formal-moduli} has a tangent dg Lie
algebra
\[
\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA},
\]
and hence a canonically attached completed module category
\[
\operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA}).
\]
For the Yangian $\Eone$-chiral algebra
\[
\cA=\mathcal{Y}(\mathfrak{sl}_N),
\]
this gives an unconditional H-level dg target for DK-4/5.

Equivalently, the live Yangian MC4 problem is not the existence of an
H-level dg target.  It is the identification of this canonical formal
moduli target with an RTT-adapted dg model whose finite quotients
recover the theorematic RTT stages and whose degree-$2$ twisting
morphism matches the ordered bar seed on the fundamental line.
\end{proposition}

\begin{proof}
Existence of the tangent dg Lie algebra $\mathfrak{g}_{\cA}$ is exactly
the content of Lurie's formal moduli theorem, as recalled in
Definition~\ref{def:factorization-formal-moduli}.  The completed module
category $\operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ is
therefore canonically attached to $\cA$.  Specializing to the Yangian
$\Eone$-chiral algebra gives the claimed H-level target.

The remaining sentence is a reformulation of the Yangian MC4 frontier:
the unresolved step is to identify the canonical target
$\mathfrak{g}_{\cA}$ with an RTT-adapted dg model, not to construct the
target itself.
\end{proof}

\begin{proposition}[Canonical associative dg model of the Yangian
formal-moduli target; \ClaimStatusProvedHere]
\label{prop:yangian-canonical-envelope}
Let
\[
\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA}
\]
be the tangent dg Lie algebra of the factorization formal moduli
problem.  Let
\[
U^{\mathrm{comp}}(\mathfrak{g}_{\cA})
\]
denote the completion of its universal enveloping dg algebra with
respect to the adic filtration defining complete
$\mathfrak{g}_{\cA}$-modules.  Then
$U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ is a canonically attached
separated complete dg algebra, and there is a canonical equivalence
\[
\operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})
\;\simeq\;
\operatorname{Mod}^{\mathrm{comp}}\bigl(
  U^{\mathrm{comp}}(\mathfrak{g}_{\cA})
\bigr).
\]
For the Yangian $\Eone$-chiral algebra, this gives an unconditional
canonical associative dg model of the H-level target.
\end{proposition}

\begin{proof}
The universal enveloping construction extends functorially to dg Lie
algebras.  Completing with respect to the same adic filtration that
defines the completed module category of the formal moduli problem
produces a separated complete dg algebra
$U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$.

By the universal property of the enveloping algebra, an action of the
dg Lie algebra $\mathfrak{g}_{\cA}$ on a complete dg module is
equivalent to an action of
$U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ on the same object, and the
intertwining morphisms are identical on both sides.  Hence the
completed module categories are canonically equivalent.  Specializing
to the Yangian $\Eone$-chiral algebra gives the claimed canonical
associative dg model.
\end{proof}

\begin{conjecture}[DK-4 as tangent Lie algebra identification;
\ClaimStatusConjectured]
\label{conj:dk4-formal-moduli}
\index{Drinfeld--Kohno!DK-4!formal moduli identification}
\index{dg-shifted Yangian!as tangent Lie algebra}
For the Yangian $\Eone$-chiral algebra
$\cA = \mathcal{Y}(\mathfrak{sl}_N)$:
\begin{enumerate}[label=\textup{(\alph*)}]
\item The tangent Lie algebra
  $\mathfrak{g}_{\cA} = T_{*}\mathfrak{F}_{\cA}$
  is quasi-isomorphic, as a filtered complete dg Lie algebra, to the
  dg-shifted Yangian $\Ydg_{\cA}$ of
  Definition~\textup{\ref{def:dg-shifted-yangian}}.
\item Under this identification, the RTT-adapted filtration
  \textup{(}Definition~\textup{\ref{def:rtt-adapted-filtration}}\textup{)}
  corresponds to the canonical filtration on
  $\mathfrak{g}_{\cA}$ by order of the formal parameter: the $N$-th
  quotient $\mathfrak{g}_{\cA}/F^{N+1}$ is the tangent Lie algebra
  of the $N$-th infinitesimal neighborhood of the identity in the
  factorization group.
\item The module category equivalence
  $\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA}) \simeq
  \operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\cA)$
  is the linearization of the formal moduli problem:
  completed modules over the tangent Lie algebra classify
  infinitesimal deformations of factorization modules.
\end{enumerate}
\end{conjecture}

\begin{remark}[Relation to existing DK-4 reductions]
\label{rem:dk4-formal-moduli-vs-rtt}
\index{Drinfeld--Kohno!DK-4!formal moduli vs RTT}
Conjecture~\ref{conj:dk4-formal-moduli} provides a \emph{canonical}
construction of the dg-shifted Yangian, replacing the specific
RTT-adapted filtration of
Definition~\ref{def:rtt-adapted-filtration} with the universal
construction from formal moduli theory.  The two approaches are
related:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The tangent Lie algebra $\mathfrak{g}_{\cA}$ exists
  unconditionally by Lurie's theorem; the content of
  Conjecture~\ref{conj:dk4-formal-moduli}(a) is that it has the
  specific algebraic structure of the dg-shifted Yangian.
\item The residue reductions of
  Proposition~\ref{prop:yangian-dk4-typea-frontier} are
  \emph{derived} from the formal moduli identification:
  the auxiliary-kernel identity $L_a(u) = R_{0a}(u-a)$ is
  the tangent-space computation of the moduli problem
  restricted to the fundamental evaluation line.
\item The RTT-adapted filtration of
  Definition~\ref{def:rtt-adapted-filtration} is the
  \emph{coordinate expression} of the canonical formal-moduli
  filtration in the basis provided by the RTT generators.
\end{enumerate}
This reformulation clarifies the logical structure: the RTT
identities are not independent axioms but consequences of the
universal $\infty$-categorical framework applied to the specific
$\Eone$-chiral algebra~$\mathcal{Y}(\mathfrak{sl}_N)$.
\end{remark}

\begin{conjecture}[DK-5 via \texorpdfstring{$\infty$}{infinity}-categorical PBW;
\ClaimStatusConjectured]
\label{conj:dk5-infty-pbw}
\index{Drinfeld--Kohno!DK-5!PBW argument}
\index{PBW theorem!infinity-categorical@$\infty$-categorical}
Assume Conjecture~\textup{\ref{conj:dk4-formal-moduli}(a,b)}.
The full triple bridge
\textup{(}Conjecture~\textup{\ref{conj:full-dk-bridge}}\textup{)}
reduces to a single input: the $\infty$-categorical
Poincar\'e--Birkhoff--Witt theorem for the factorization Lie
algebra~$\mathfrak{g}_{\cA}$.
\begin{enumerate}[label=\textup{(\alph*)}]
\item The formal group
  $G_{\cA} := \exp(\mathfrak{g}_{\cA})$
  is a group object in $\Eone$-factorization coalgebras on
  $\operatorname{Ran}(X)$.  Its representation category
  $\operatorname{Rep}(G_{\cA})$ is a braided monoidal stable
  $\infty$-category.
\item The $\infty$-categorical PBW theorem gives an equivalence
  \[
  \operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})
  \;\simeq\;
  \operatorname{Rep}(G_{\cA})
  \]
  between completed modules over the Lie algebra and
  representations of the formal group.
\item If $G_{\cA} \simeq \QGspec(R_{\cA})$
  \textup{(}the spectral quantum group of
  Latyntsev~\cite{Latyntsev23}\textup{)}, then the full triple
  equivalence~\eqref{eq:triple-equivalence} follows from the chain
  \begin{multline*}
  \Factord(X;\cA)
  \;\xleftarrow[\textup{DK-3}]{\sim}\;
  \operatorname{CoFact}_{\Eone}(\cA^{!,c})^{\mathrm{op}}
  \\
  \;\xrightarrow[\textup{PBW}]{\sim}\;
  \operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})
  \;\xrightarrow[\exp]{\sim}\;
  \operatorname{Rep}(\QGspec(R_{\cA}))^{\mathrm{op}}.
  \end{multline*}
\end{enumerate}
\end{conjecture}

\begin{remark}[The DK ladder as successive approximation to
\texorpdfstring{$\infty$}{infinity}-categorical Koszul duality]
\label{rem:unified-dk-hierarchy}
\index{Drinfeld--Kohno!unified hierarchy}
The five DK levels are successive approximations to $\infty$-categorical Koszul duality for $\cA = \mathcal{Y}(\fg)$:
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{lll}
\textbf{Level} & \textbf{Content} & \textbf{Status} \\
\hline
DK-0 & Chain-level Koszul duality on $\operatorname{Ran}_1$
  & \textbf{Proved} \\
DK-1 & Extension to $\operatorname{Ran}_n$ on evaluation objects
  & \textbf{Proved} \\
DK-2/3 & Extension to generated core (sectorwise convergence)
  & \textbf{Proved} \\
DK-4 & Tangent Lie algebra $=$ dg-shifted Yangian (Conjecture~\ref{conj:dk4-formal-moduli})
  & Conjectured \\
DK-5 & $\infty$-PBW: Lie modules $\simeq$ group representations (Conjecture~\ref{conj:dk5-infty-pbw})
  & Conjectured \\
\end{tabular}
\end{center}
DK-0/1 is classical (Drinfeld--Kohno $+$ Kazhdan--Lusztig); DK-2/3 extends via Boardman convergence of the loop spectral sequence (Theorem~\ref{thm:h-level-factorization-kd}); DK-4 is the formal moduli step; DK-5 requires the exponential $\mathfrak{g}_{\cA} \to G_{\cA}$ recovering the spectral quantum group of Latyntsev~\cite{Latyntsev23}.  Contributing to Conjecture~\ref{conj:master-dk-kl}.
\end{remark}

\begin{remark}[The RTT relation as Koszul duality datum]
\label{rem:rtt-is-the-duality-datum}
\index{Yangian!RTT as Koszul datum}
\index{Koszul duality!engine of DK ladder}
The entire proved DK ladder (DK-0 through DK-3, unconditional at
all simple types) rests on a single structural observation:
\smallskip
\begin{center}
\emph{The RTT relation
$R_{12}(u\!-\!v)\,T_1(u)\,T_2(v)
= T_2(v)\,T_1(u)\,R_{12}(u\!-\!v)$
is simultaneously the defining relation of the algebra
and the input to Koszul duality.}
\end{center}

\smallskip\noindent
Three consequences, each one sentence, give the full result:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Quadratic $\Rightarrow$ $R$-matrix inversion.}
  The RTT relation is quadratic in~$T$; the orthogonal complement
  $R^\perp$ of the $R(u)$-relations is the $R^{-1}(u)$-relations,
  so $Y(\fg)^! = Y_{-\hbar}(\fg)$
  (Theorem~\ref{thm:yangian-koszul-dual}).

\item \emph{PBW $\Rightarrow$ Koszulness.}
  Molev's PBW basis gives a flat deformation to
  $\operatorname{Sym}(V)$; $\operatorname{Sym}$ is classically
  Koszul; flatness transfers Koszulness to~$Y(\fg)$, giving
  bar-cobar recovery for free
  (Proposition~\ref{prop:yangian-koszul},
  Corollary~\ref{cor:yangian-bar-cobar}).

\item \emph{Root grading $\Rightarrow$ sectorwise convergence.}
  The root lattice $Q(\fg)$ decomposes the bar complex into sectors
  with $\dim V_r = (\dim V_0)^2$ uniformly; a non-increasing
  sequence of non-negative integers stabilizes; the factorization
  bar complex is therefore a genuine coalgebra on
  $\operatorname{Ran}(X)$, and K\"unneth $+$ cosheaf descent extend
  the diagonal quasi-isomorphism to all strata
  (Theorem~\ref{thm:sectorwise-spectral-convergence},
  Theorem~\ref{thm:h-level-factorization-kd}).
\end{enumerate}
These are logically independent inputs; together they give DK-2/3
for every simple~$\fg$ without any thick-generation argument.

The deeper unity: all three are consequences of the fact that
\emph{the RTT presentation expresses the Yangian as a quadratic
algebra whose defining relations encode the $R$-matrix}.
The bar construction extracts the $R$-matrix and inverts it;
PBW guarantees this extraction is lossless; the root grading
guarantees it converges sector by sector.  Geometrically:
bar-cobar duality is Verdier duality on ordered configuration
spaces, and Verdier duality reverses the orientation of ordered
collisions --- which inverts the $R$-matrix.  The RTT presentation
is, in this precise sense, the Yangian \emph{presenting itself as
a Koszul duality problem}.

For the conjectural levels: DK-4 adds no new idea.
The same PBW--Koszul--root-grading package gives surjective
transition maps $\bigwedge^n(V_{\leq N+1}^*) \twoheadrightarrow
\bigwedge^n(V_{\leq N}^*)$ on the associated graded of bar
cohomology, hence Mittag-Leffler for the RTT tower
(Theorem~\ref{thm:rtt-mittag-leffler}) and a well-behaved
completed bar-cobar equivalence
(Corollary~\ref{cor:completed-bar-cobar-yangian}).
What remains is a structure identification:
$\varprojlim_N \fg_N \cong \Ydg_\cA$
(Maurer--Cartan element, translation, coproduct).
DK-5 adds only the $\infty$-categorical PBW exponential
$\operatorname{Mod}(\fg_\cA) \simeq
\operatorname{Rep}(\exp(\fg_\cA))$.
\end{remark}

\subsubsection*{Coderived factorization duality off the Koszul locus}

On the Koszul locus (generic levels, evaluation-generated core),
Theorem~\ref{thm:h-level-factorization-kd} provides an equivalence
in the ordinary derived sense.  Off the Koszul locus --- at admissible
affine levels, minimal-model central charges, or for infinite-dimensional
modules beyond the generated core --- the bar-cobar object persists as a
\emph{curved} factorization coalgebra, and the correct framework is the
coderived/contraderived category of
Positselski~\cite{Positselski11}.

\begin{theorem}[Factorization Positselski equivalence; \ClaimStatusProvedHere]
\label{thm:factorization-positselski}
\index{Positselski!factorization equivalence|textbf}
\index{coderived category!factorization|textbf}
\index{bar-cobar duality!off the Koszul locus}
Let~$\cA$ be an $\Eone$-chiral algebra on~$X$ satisfying
hypotheses~\ref{h2:sectorwise} and~\ref{h3:convergence} of
Theorem~\textup{\ref{thm:h-level-factorization-kd}}
\textup{(}sectorwise finiteness and spectral convergence\textup{)},
but not necessarily~\ref{h1:koszulness}
\textup{(}$\Eone$-Koszulness\textup{)}.
Let $C = \barB^{\mathrm{fact}}(\cA)$ denote the curved factorization
bar coalgebra.  Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item The factorization coderived category
  $D^{\mathrm{co}}(C\text{-}\mathrm{CoFact}_{\Eone}^{\mathrm{conil}})$
  is a well-defined stable $\infty$-category: the sectorwise
  finiteness of~$C$ ensures that each $Q(\fg)$-sector is a
  genuine conilpotent coalgebra \textup{(}not a formal
  pro-object\textup{)}, so the coacyclicity localizing
  subcategory is well-defined.
\item There is a triangulated equivalence
  \begin{equation}\label{eq:factorization-positselski}
  D^{\mathrm{co}}\bigl(
    C\text{-}\mathrm{CoFact}_{\Eone}^{\mathrm{conil}}
  \bigr)
  \;\simeq\;
  D^{\mathrm{ctr}}\bigl(
    \cA^!\text{-}\mathrm{ContraFact}_{\Eone}^{\mathrm{comp}}
  \bigr),
  \end{equation}
  where the left side is the coderived category of conilpotent
  $\Eone$-factorization comodules over~$C$, and the right side is
  the contraderived category of complete \textup{(}pro-nilpotent\textup{)}
  $\Eone$-factorization contramodules over~$\cA^!$.
\item On the Koszul locus \textup{(}when~\ref{h1:koszulness}
  also holds\textup{)}, the coderived and ordinary derived categories
  coincide on compact objects, and~\eqref{eq:factorization-positselski}
  restricts to the equivalence of
  Theorem~\textup{\ref{thm:h-level-factorization-kd}(iii)}.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Part~(i).}
Sectorwise finiteness (hypothesis~\ref{h2:sectorwise}) gives
$C = \bigoplus_{\gamma} C_\gamma$ with each $C_\gamma$
finite-dimensional over each $\operatorname{Ran}$-stratum.
The factorization structure on~$C$ preserves the
$Q(\fg)$-grading (Proposition~\ref{prop:yangian-bar-loop-weight}(a)),
so the coaugmentation filtration
$F_0 C \subset F_1 C \subset \cdots$ has each
$F_n C_\gamma$ finite-dimensional.  The conilpotency condition
$C = \bigcup_n F_n C$ then holds sector-by-sector, and the
coacyclicity localizing subcategory (thick closure of totalizations
of exact triples, closed under coproducts) is well-defined
by the same argument as
Definition~\ref{def:chiral-coderived}, applied sectorwise.

\emph{Part~(ii).}
The chain-level comodule-contramodule correspondence
(Theorem~\ref{thm:chiral-co-contra-correspondence}) provides the
equivalence on
$\operatorname{Ran}_1(X) \cong X$.  The factorization structure
propagates this to $\operatorname{Ran}_n$ by the same
K\"unneth--descent argument as
Theorem~\ref{thm:h-level-factorization-kd}(i):
on disjoint opens the equivalence decomposes as a tensor product
of chain-level equivalences, and the factorization cosheaf
condition extends to overlapping configurations.  Sectorwise
finiteness ensures the tensor products are well-defined
(no infinite-dimensionality obstructions).

\emph{Part~(iii).}
On the Koszul locus, the curvature vanishes:
$h = m_0^{(g)} = 0$ at genus~$0$
(Theorem~\ref{thm:higher-genus-inversion}(a)).  When $h = 0$,
coacyclic = acyclic (Positselski~\cite[Thm~3.7]{Positselski11}),
so $D^{\mathrm{co}} = D^b$ on compact objects.  The restriction
of~\eqref{eq:factorization-positselski} to compacts recovers
Theorem~\ref{thm:h-level-factorization-kd}(iii).
\end{proof}

\begin{remark}[The coderived category as the natural ambient]
\label{rem:coderived-natural-ambient}
\index{coderived category!as natural ambient for DK}
The equivalence~\eqref{eq:factorization-positselski} is the
\emph{correct categorical context} for the full MC3 programme:
\begin{enumerate}[label=\textup{(\alph*)}]
\item On the Koszul locus (generic level), DK-0 through DK-3
  live in the ordinary derived category, and the coderived
  category adds nothing new.  This is the domain of
  Theorem~\ref{thm:h-level-factorization-kd}.
\item Off the Koszul locus (admissible levels, minimal-model central
  charges), the bar-cobar object~$\Omega(C)$ is curved:
  $d^2 = h \neq 0$.  The ordinary derived category is trivial
  (every module is contractible via $h$), but the coderived
  category retains the full categorical information.
  The four conjectures of
  Remark~\ref{rem:corrected-mc3-frontier}(b)
  naturally live here: Baxter exact triangles, shifted-prefundamental
  generation, pro-Weyl recovery, and DK on compacts are all
  statements about the coderived/contraderived
  equivalence~\eqref{eq:factorization-positselski}.
\item The passage from the evaluation-generated core (compact objects
  in $D^b$) to the full category~$\mathcal{O}$ (possibly
  non-compact objects in $D^{\mathrm{co}}$) is controlled by the
  ind-completion of the coderived category: see
  Theorem~\ref{thm:ind-completed-extension} below.
\end{enumerate}
\end{remark}

\subsubsection*{Ind-completed factorization extension}

The extension from the evaluation-generated core (compact objects)
to the full Yangian category~$\mathcal{O}$ (ind-completed)
is a standard categorical construction once the compact part is
established.  The key input is the
\emph{compactness of evaluation objects} in the factorization
category.

\begin{theorem}[Ind-completed factorization DK equivalence; \ClaimStatusProvedHere]
\label{thm:ind-completed-extension}
\index{ind-completion!factorization DK|textbf}
\index{Drinfeld--Kohno!ind-completed extension}
Under the hypotheses of
Theorem~\textup{\ref{thm:h-level-factorization-kd}},
the equivalence on evaluation-generated cores extends uniquely
to an equivalence of ind-completed categories:
\begin{equation}\label{eq:ind-completed-dk}
\operatorname{Ind}\bigl(
  \operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\cA)
\bigr)
\;\simeq\;
\operatorname{Ind}\bigl(
  \operatorname{CoFact}_{\Eone}^{\mathrm{gen}}(\cA^{!,c})
  ^{\mathrm{op}}
\bigr).
\end{equation}
This ind-completed category is presentable, stable, and admits
a canonical $t$-structure whose heart contains the abelian
category~$\mathcal{O}$.
\end{theorem}

\begin{proof}
The evaluation-generated core
$\operatorname{Fact}_{\Eone}^{\mathrm{gen}}(\cA)$ is a small,
idempotent-complete, stable $\infty$-category
(Proposition~\ref{prop:yangian-dk3-generated-core}).  The
equivalence of Theorem~\ref{thm:h-level-factorization-kd}(iii) is
an exact functor between small stable $\infty$-categories.  By
the universal property of ind-completion
(Lurie~\cite[Prop.~5.3.5.10]{HTT}), any exact equivalence between
small stable $\infty$-categories extends uniquely to a
colimit-preserving equivalence between their ind-completions.
This gives~\eqref{eq:ind-completed-dk}.

Presentability follows from $\operatorname{Ind}(\mathcal{C})$
being presentable whenever $\mathcal{C}$ is small and
idempotent-complete (Lurie~\cite[Prop.~5.5.7.8]{HTT}).
Stability is preserved by ind-completion.

The $t$-structure: evaluation objects are
bounded (finite-length in the heart of category~$\mathcal{O}$),
so they generate a bounded $t$-structure on the generated
core.  This extends to the ind-completion by
\cite[Prop.~1.3.5.21]{HA}, with heart a Grothendieck abelian
category containing~$\mathcal{O}_Y$ as a full subcategory
(via the fully faithful embedding
$\mathcal{O}_Y \hookrightarrow
\operatorname{Ind}(\operatorname{Fact}_{\Eone}^{\mathrm{gen}})$
of Theorem~\ref{thm:eval-core-identification}).
\end{proof}

\begin{remark}[Ind-completion vs.\ pro-Weyl completion]
\label{rem:ind-vs-proweyl}
\index{pro-Weyl completion!vs.\ ind-completion}
The ind-completed category
$\operatorname{Ind}(\operatorname{Fact}_{\Eone}^{\mathrm{gen}})$
is the \emph{free cocompletion} of the generated core: it
formally adds all filtered colimits.  This is a strictly larger
category than the generated core but a strictly smaller one than
the full coderived category
$D^{\mathrm{co}}(\barB^{\mathrm{fact}}\text{-}\mathrm{CoFact})$
of Theorem~\ref{thm:factorization-positselski}.

The four conjectures of
Remark~\ref{rem:corrected-mc3-frontier}(b) concern modules
that lie in the ind-completion but not in the generated core:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \emph{Standard modules} $M(\Psi)$: by
  Conjecture~\ref{conj:pro-weyl-recovery}, these are
  pro-Weyl limits $R\varprojlim_m W_m$, where each~$W_m$ is
  compact (evaluation-generated).  The pro-object
  $\{W_m\}$ defines an object of $\operatorname{Pro}(\mathcal{C})
  \hookrightarrow \operatorname{Ind}(\mathcal{C})$
  via the canonical functor
  $\operatorname{Pro}(\mathcal{C}) \to
  \operatorname{Ind}(\mathcal{C})^{\mathrm{op}}$.
\item \emph{Prefundamental modules} $L^-_{i,a}$: by
  Conjecture~\ref{conj:shifted-prefundamental-generation}, these
  are compact generators of the completed shifted category.
  In the ind-completed factorization category, $L^-_{i,a}$
  should be representable as a filtered colimit of evaluation
  objects (via the Baxter exact triangles of
  Conjecture~\ref{conj:baxter-exact-triangles}).
\end{enumerate}
The equivalence~\eqref{eq:ind-completed-dk} provides the
categorical framework in which both types of extensions live.
\end{remark}

\subsubsection*{The four conjectures in the formal moduli framework}

The formal moduli problem~$\mathfrak{F}_{\cA}$
(Definition~\ref{def:factorization-formal-moduli}) provides a
unified $\infty$-categorical formulation of the four MC3
conjectures.  Each conjecture becomes a statement about the
tangent Lie algebra~$\mathfrak{g}_{\cA}$ or the formal
group~$G_{\cA} = \exp(\mathfrak{g}_{\cA})$.

\begin{conjecture}[Formal moduli reformulation of MC3 conjectures;
\ClaimStatusConjectured]
\label{conj:mc3-formal-moduli-reformulation}
\index{MC3!formal moduli reformulation}
\index{formal moduli problem!MC3 conjectures}
The four MC3 conjectures admit the following reformulations in terms
of the factorization formal moduli problem~$\mathfrak{F}_{\cA}$
and the tangent Lie algebra
$\mathfrak{g}_{\cA} = T_{*}\mathfrak{F}_{\cA}$:
\begin{enumerate}[label=\textup{(\Roman*)}]
\item \emph{Baxter
  \textup{(}Conjecture~\textup{\ref{conj:baxter-exact-triangles}}\textup{)}
  as infinitesimal deformation exact triangles.}
  The Baxter TQ relations lift to distinguished triangles in
  the category $\operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})$
  of completed modules over the tangent Lie algebra.  The
  companion module $M_{k,x}^{(i)}$ represents the tangent
  vector to the evaluation deformation at the point
  $(k, x) \in \mathbb{C}^2$, and the TQ triangle is the
  fiber sequence of the tangent map
  $T_{(k,x)}\mathfrak{F}_{\cA} \to
  T_{(k',x')}\mathfrak{F}_{\cA}$.

\item \emph{Shifted-prefundamental generation
  \textup{(}Conjecture~\textup{\ref{conj:shifted-prefundamental-generation}}\textup{)}
  as compact generation of the tangent category.}
  The compact objects of
  $\operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})$
  are the thick closure of tangent representations at
  evaluation and prefundamental points.  In the formal moduli
  picture, these are the tangent spaces to the evaluation
  locus (compact, by the proved DK-1) and the
  prefundamental locus (conjecturally compact).

\item \emph{Pro-Weyl recovery
  \textup{(}Conjecture~\textup{\ref{conj:pro-weyl-recovery}}\textup{)}
  as completeness of the formal moduli problem.}
  For a rational $\ell$-weight~$\Psi$, the standard module
  $M(\Psi)$ is the derived global sections of the formal
  neighborhood of~$\Psi$ in the moduli of $\ell$-weights:
  \[
  M(\Psi)
  \;\simeq\;
  R\Gamma\bigl(\widehat{\mathrm{Spec}\,
  \mathcal{O}}_\Psi,\;
  \mathcal{V}_{\mathfrak{F}_{\cA}}\bigr)
  \;\simeq\;
  R\varprojlim_m\, W_m,
  \]
  where the Weyl modules~$W_m$ are the values of the moduli
  functor on the $m$-th infinitesimal neighborhood.

\item \emph{DK on compacts
  \textup{(}Conjecture~\textup{\ref{conj:dk-compacts-completion}}\textup{)}
  as formal GAGA.}
  The bar-cobar equivalence extends from the generic
  fiber (evaluation locus) to the formal neighborhood
  (completed category) by a formal GAGA principle for
  the factorization formal moduli problem:
  coherent sheaves on the formal completion agree with
  algebraic coherent sheaves on the Koszul locus.
\end{enumerate}
\end{conjecture}

\begin{remark}[Tangent Lie algebra controls the extension programme]
\label{rem:tangent-controls-extension}
\index{tangent Lie algebra!role in MC3 extension}
The formal moduli reformulation
(Conjecture~\ref{conj:mc3-formal-moduli-reformulation})
reveals the organizing role of the tangent Lie
algebra~$\mathfrak{g}_{\cA}$: all four MC3 extension
conjectures are consequences of a single structural property of
$\mathfrak{g}_{\cA}$, namely that it is \emph{algebraizable} ---
that the formal moduli problem~$\mathfrak{F}_{\cA}$ is the
formal completion of a global (algebraic) moduli problem.

In the DK-4 framework
(Conjecture~\ref{conj:dk4-formal-moduli}), algebraizability is the
content of the RTT-adapted filtration: the formal
group~$G_{\cA}$ admits a filtration whose finite quotients are
the finite RTT stages, and the transition maps are the RTT
truncations.  If this filtration is Mittag-Leffler on cohomology
(the concrete form of algebraizability), all four conjectures
follow by the MC4 reduction principle
(Conjecture~\ref{conj:inverse-limit-completed-bar-cobar}).

This reduces the four MC3 conjectures to a single input:
\emph{the Mittag-Leffler property of the RTT tower on bar
cohomology.}
\end{remark}

\subsubsection*{Factorization DK-4: tangent Lie algebra via
bar derivations}

Conjecture~\ref{conj:dk4-formal-moduli} identifies DK-4 with the
tangent Lie algebra computation
$\mathfrak{g}_{\cA} \simeq \Ydg_{\cA}$.
The following proposition provides the first constructive step:
the tangent Lie algebra at finite RTT stage is computable,
and the compatibility of these finite computations is the
content of DK-4.

\begin{proposition}[Finite-stage tangent Lie algebras;
\ClaimStatusProvedHere]
\label{prop:finite-stage-tangent}
\index{tangent Lie algebra!finite RTT stage}
\index{dg-shifted Yangian!finite-stage construction}
For the Yangian $\Eone$-chiral algebra
$\cA = \mathcal{Y}(\fg)$ and the $N$-th RTT truncation
$\cA_{\leq N}$, the tangent Lie algebra
$\mathfrak{g}_N := T_{*}\mathfrak{F}_{\cA_{\leq N}}$
satisfies:
\begin{enumerate}[label=\textup{(\alph*)}]
\item $\mathfrak{g}_N$ is a finite-dimensional dg Lie algebra
  with $N \cdot (\dim V_0)^2$ generators in degree~$0$
  \textup{(}one copy of $\operatorname{End}(V_0)$ per RTT
  level; for the reduced Yangian, $N \cdot \dim \fg$
  generators\textup{)}.
\item The differential on~$\mathfrak{g}_N$ is the derivation
  of $\barB(\cA_{\leq N})$ induced by the bar differential:
  \[
  \mathfrak{g}_N
  \;\cong\;
  \operatorname{Der}^{\mathrm{cont}}\bigl(
    \barB(\cA_{\leq N}),\, \barB(\cA_{\leq N})
  \bigr)[1].
  \]
\item The truncation maps $\cA_{\leq N+1} \to \cA_{\leq N}$
  induce surjective dg Lie algebra maps
  $\mathfrak{g}_{N+1} \twoheadrightarrow \mathfrak{g}_N$,
  compatible with the bar construction.
\item At $N = 1$, $\mathfrak{g}_1 \cong \mathfrak{gl}(V_0)$
  \textup{(}the RTT generators $T_{ij}^{(0)}$ at level~$0$ span
  $\operatorname{End}(V_0)$ with the commutator bracket\textup{)},
  concentrated in degree~$0$.  For the reduced Yangian
  $Y(\fg)$ \textup{(}quantum determinant quotient\textup{)},
  $\mathfrak{g}_1 \cong \fg$.
\end{enumerate}
\end{proposition}

\begin{proof}
Part~(a):
$\cA_{\leq N}$ is the quotient of~$\cA$ by generators of
level $> N$.  Each level contributes $(\dim V_0)^2$
generators (the RTT modes $T_{ij}^{(r)}$ for
$0 \leq r \leq N-1$), so $\mathfrak{g}_N$ has
$N \cdot (\dim V_0)^2$ generators in degree~$0$.
Since $\cA_{\leq N}$ is quadratic and Koszul
(Proposition~\ref{prop:yangian-koszul}), the tangent Lie
algebra $\mathfrak{g}_N \cong
\operatorname{Ext}^*_{\cA_{\leq N}}(\bC, \bC)[1]$ is
finite-dimensional (each degree of the Koszul dual
$\cA_{\leq N}^!$ is finite-dimensional by local finiteness).

Part~(b):
By Lurie's formal moduli theorem~\cite{LurieDAGX}, the tangent
Lie algebra is computed as the shifted derivations of the bar
coalgebra.  For the finite-dimensional quotient~$\cA_{\leq N}$,
the bar coalgebra $\barB(\cA_{\leq N})$ is finite-dimensional
(bounded bar degree by the quadratic relations), so
the derivation complex is finite-dimensional.

Part~(c):
The truncation map $\cA_{\leq N+1} \twoheadrightarrow \cA_{\leq N}$
induces a surjection
$\barB(\cA_{\leq N+1}) \twoheadrightarrow \barB(\cA_{\leq N})$
of bar coalgebras (bar is covariant on algebra maps).

For the tangent Lie algebras, the map
$\mathfrak{g}_{N+1} \to \mathfrak{g}_N$ is surjective by the
following Koszul dual argument: since $\cA_{\leq N}$ is Koszul,
the tangent Lie algebra in degree~$p$ is
$(\mathfrak{g}_N)_p \cong (\cA_{\leq N}^!)_{p+1}$.

The Koszul dual $\cA_{\leq N}^!$ has generators
$V_{\leq N}^*$ and relations $R_{\leq N}^\perp$.
Any element $f \in (\cA_{\leq N}^!)_n
\subset (V_{\leq N}^*)^{\otimes n} \cap (R_{\leq N}^\perp)_n$
extends by zero on the $V_N^*$-components to an element
$\tilde{f} \in (\cA_{\leq N+1}^!)_n$
(since $\tilde{f}$ automatically annihilates all
relations involving level-$N$ generators).
Hence $(\cA_{\leq N+1}^!)_n \twoheadrightarrow (\cA_{\leq N}^!)_n$
is surjective in every degree.

The identification
$(\mathfrak{g}_N)_p \cong (\cA_{\leq N}^!)_{p+1}$ is natural
in~$N$: it arises from Lurie's formal moduli theorem (Part~(b))
applied to each truncation, and the truncation-compatible maps of
bar coalgebras induce compatible maps on derivation complexes.
Thus the surjectivity of $(\cA_{\leq N+1}^!)_n \twoheadrightarrow
(\cA_{\leq N}^!)_n$ directly yields
$\mathfrak{g}_{N+1} \twoheadrightarrow \mathfrak{g}_N$ in every
internal degree.

Part~(d):
At $N = 1$, $\cA_{\leq 1} \cong U(\mathfrak{gl}(V_0))$ (the
$T_{ij}^{(0)}$ for $1 \leq i,j \leq \dim V_0$ generate
$\operatorname{End}(V_0) = \mathfrak{gl}(V_0)$ under the
commutator, and the RTT relation at level~$0$ reproduces the
$\mathfrak{gl}(V_0)$ bracket).  The bar complex
$\barB(U(\mathfrak{gl}(V_0)))$ is the Chevalley--Eilenberg complex,
and $\operatorname{Der}(\barB(U(\mathfrak{gl}(V_0))))[1]
\cong \mathfrak{gl}(V_0)$, concentrated in degree~$0$.
The quantum determinant condition at level~$0$ reduces the
identity component, giving $\mathfrak{g}_1 \cong \fg$ for
the reduced Yangian.
\end{proof}

\begin{theorem}[Mittag-Leffler for the RTT bar cohomology tower;
\ClaimStatusProvedHere]
\label{thm:rtt-mittag-leffler}
\index{Mittag-Leffler condition!RTT tower|textbf}
\index{bar complex!RTT tower!Mittag-Leffler}
\index{Drinfeld--Kohno!DK-4!Mittag-Leffler}
For any simple Lie algebra~$\fg$, the transition maps on bar
cohomology in the RTT tower are surjective:
\[
H^n\bigl(\barB(\cA_{\leq N+1})\bigr)
\;\twoheadrightarrow\;
H^n\bigl(\barB(\cA_{\leq N})\bigr)
\qquad \text{for all } N \geq 1, \;\text{all } n \geq 0.
\]
In particular, the Mittag-Leffler condition holds and
$\varprojlim^1_N H^n(\barB(\cA_{\leq N})) = 0$.
\end{theorem}

\begin{proof}
\emph{Step~1: PBW filtration on truncated bar complexes.}
Each truncation $\cA_{\leq N} = Y(\fg)_{\leq N}$ inherits the
PBW filtration of Proposition~\ref{prop:yangian-koszul}:
$F_p \cA_{\leq N}$ is spanned by ordered monomials of total
level $\leq p$ in the RTT generators $\{T_{ij}^{(r)}\}_{r < N}$.
The associated graded is the polynomial algebra:
\[
\operatorname{gr}_F \cA_{\leq N}
\;\cong\;
\operatorname{Sym}(V_{\leq N}),
\qquad
V_{\leq N} = \bigoplus_{r=0}^{N-1}
\operatorname{End}(\bC^{N_0})_r,
\]
where $N_0 = \dim V_0$.  The truncation maps
$\cA_{\leq N+1} \twoheadrightarrow \cA_{\leq N}$ preserve the
PBW filtration and induce the projection
$\operatorname{Sym}(V_{\leq N+1}) \twoheadrightarrow
\operatorname{Sym}(V_{\leq N})$ on associated graded.

\emph{Step~2: PBW spectral sequence for bar cohomology.}
The PBW filtration induces a bounded-below, exhaustive filtration
on $\barB(\cA_{\leq N})$.  By
Theorem~\ref{thm:pbw-koszulness-criterion} (``bar construction
commutes with taking associated graded for flat filtrations''),
the associated spectral sequence has $E_1$ page
\[
E_1^{p,q}(\cA_{\leq N})
= H^{p+q}\bigl(\barB(\operatorname{Sym}(V_{\leq N}))\bigr).
\]
By Koszulness of $\cA_{\leq N}$
(Proposition~\ref{prop:yangian-koszul} applies to each truncation:
$\cA_{\leq N}$ is a quadratic algebra in finitely many generators
$\{T_{ij}^{(r)}\}_{r < N}$ with the restricted RTT relations, inherits
the PBW basis of Molev, and satisfies local finiteness a~fortiori),
the spectral sequence \emph{degenerates at $E_1$}:
$E_1 = E_\infty$.  Indeed, Koszulness forces bar cohomology
onto the diagonal $p + q = n$, $p = n$ (homological = internal
degree), so all higher differentials $d_r$ for $r \geq 2$ have
zero source or target for bidegree reasons.

\emph{Step~3: Surjectivity on $E_1$.}
For the commutative algebra $\operatorname{Sym}(V_{\leq N})$,
the Koszul dual is $\bigwedge(V_{\leq N}^*)$, and bar cohomology
in degree~$n$ is $\bigwedge^n(V_{\leq N}^*)$.  The truncation
$\operatorname{Sym}(V_{\leq N+1}) \twoheadrightarrow
\operatorname{Sym}(V_{\leq N})$ induces on bar cohomology the
projection
\[
\textstyle
\bigwedge\nolimits^n(V_{\leq N+1}^*)
\;\twoheadrightarrow\;
\bigwedge\nolimits^n(V_{\leq N}^*),
\]
which kills exactly the wedge products involving the factor
$\operatorname{End}(\bC^{N_0})_N^*$.  This map is surjective
for all $N$ and $n$.

\emph{Step~4: Filtered surjectivity implies surjectivity.}
The truncation maps $\cA_{\leq N+1} \to \cA_{\leq N}$ are
compatible with the PBW filtrations, hence induce a map of
spectral sequences.  On the $E_1 = E_\infty$ page, this map
is the surjection of Step~3.  Since the PBW filtration on
$H^n(\barB(\cA_{\leq N}))$ is exhaustive and bounded below
(each bar degree and level contributes finitely), a standard
filtered-surjectivity argument gives: a filtered map
$f\colon M' \to M$ of filtered objects inducing a surjection
$\operatorname{gr}_p f$ on each graded piece is itself
surjective.  (Proof: by induction on $p$, the image of
$f$ contains $F_p M$ for each~$p$; exhaustivity gives
$\operatorname{im}(f) = M$.)

Therefore $H^n(\barB(\cA_{\leq N+1}))
\twoheadrightarrow H^n(\barB(\cA_{\leq N}))$
is surjective for all $N$ and~$n$.  Surjective transition maps
trivially satisfy Mittag-Leffler, giving
$\varprojlim^1 = 0$.
\end{proof}

\begin{corollary}[Completed bar-cobar equivalence for Yangians;
\ClaimStatusProvedHere]
\label{cor:completed-bar-cobar-yangian}
\index{bar-cobar duality!completed Yangian|textbf}
\index{Yangian!completed bar-cobar}
For any simple~$\fg$, the completed reduced bar construction
\[
\widehat{\barB}\bigl(Y(\fg)\bigr)
\;:=\;
\varprojlim_N\, \barB\bigl(Y(\fg)_{\leq N}\bigr)
\]
exists as a separated complete conilpotent $\Eone$-chiral coalgebra,
and the completed cobar-bar counit is a quasi-isomorphism:
\[
\Omega^{\mathrm{ch}}\bigl(
  \widehat{\barB}(Y(\fg))
\bigr)
\;\xrightarrow{\;\sim\;}\;
Y(\fg).
\]
This resolves
Conjecture~\textup{\ref{conj:inverse-limit-completed-bar-cobar}}
for the Yangian RTT tower.
\end{corollary}

\begin{proof}
The three hypotheses of
Conjecture~\ref{conj:inverse-limit-completed-bar-cobar} are verified:
\begin{enumerate}[label=\textup{(\roman*)}]
\item Each truncation $\cA_{\leq N}$ is finite type and lies in
  the proved bar-cobar regime
  (Corollary~\ref{cor:yangian-bar-cobar}).
\item The transition maps $\cA_{\leq N+1} \to \cA_{\leq N}$ are
  compatible with the finite-stage bar constructions
  (PBW filtration compatibility,
  Proposition~\ref{prop:finite-stage-tangent}(c)).
\item The inverse system on bar complexes satisfies Mittag-Leffler
  (Theorem~\ref{thm:rtt-mittag-leffler}): the transition maps
  on bar cohomology are surjective, so
  $\varprojlim^1_N H^n(\barB(\cA_{\leq N})) = 0$.
\end{enumerate}
The Mittag-Leffler condition gives
$H^n(\widehat{\barB}(Y(\fg)))
\cong \varprojlim_N H^n(\barB(\cA_{\leq N}))$
(no $\varprojlim^1$ correction).  The completed cobar differential
is continuous by
Proposition~\ref{prop:inverse-limit-differential-continuity}
(automatic for inverse systems of finite-stage curved dg
coalgebras).  By the MC4 reduction principle
(Proposition~\ref{prop:mc4-reduction-principle},
now verified for this tower), the completed cobar-bar counit
restricts at each finite stage to the proved
quasi-isomorphism
$\Omega(\barB(\cA_{\leq N})) \xrightarrow{\sim} \cA_{\leq N}$,
and the Mittag-Leffler condition ensures the inverse limit
of quasi-isomorphisms is a quasi-isomorphism.
\end{proof}

\begin{conjecture}[DK-4: tangent Lie algebra identification;
\ClaimStatusConjectured]
\label{conj:dk4-inverse-limit}
\index{Drinfeld--Kohno!DK-4!inverse limit construction}
\index{tangent Lie algebra!inverse limit}
By Theorem~\textup{\ref{thm:rtt-mittag-leffler}}, the
inverse system $\{\mathfrak{g}_N\}_{N \geq 1}$ of
Proposition~\textup{\ref{prop:finite-stage-tangent}} satisfies
Mittag-Leffler with surjective transition maps, and the tangent
Lie algebra of the factorization formal moduli problem is
\[
\mathfrak{g}_{\cA}
\;=\;
T_{*}\mathfrak{F}_{\cA}
\;\cong\;
\varprojlim_N\, \mathfrak{g}_N.
\]
The remaining content of DK-4 is the identification of this
inverse limit with the dg-shifted Yangian:
\[
\varprojlim_N\, \mathfrak{g}_N
\;\cong\;
\Ydg_{\cA}.
\]
This identification is equivalent to showing that the derivation
complex $\operatorname{Der}(\widehat{\barB}(Y(\fg)))$
carries the dg-shifted RTT structure
\textup{(}Definition~\textup{\ref{def:dg-shifted-yangian}}\textup{)}:
the Maurer--Cartan element $r(z) = \tau|_{\deg 2}$, the
translation operator, and the twisted coproduct.
\end{conjecture}

\begin{remark}[DK-4 reduced to structure identification]
\label{rem:dk4-mittag-leffler}
\index{Mittag-Leffler condition!DK-4 reduction}
Theorem~\ref{thm:rtt-mittag-leffler} and
Corollary~\ref{cor:completed-bar-cobar-yangian} resolve the
\emph{analytic} part of DK-4: the inverse limit exists, is
well-behaved ($\varprojlim^1 = 0$), and the completed bar-cobar
equivalence holds.  What remains is the \emph{algebraic}
identification of $\varprojlim_N \mathfrak{g}_N$ with the
dg-shifted Yangian --- specifically, the three structural
data:
\begin{enumerate}[label=\textup{(\alph*)}]
\item the Maurer--Cartan element $r(z)$ arises as the
  degree-$2$ part of the bar propagator~$\tau$;
\item the translation operator is the derivation induced by
  $T_{ij}^{(r)} \mapsto T_{ij}^{(r+1)}$;
\item the twisted coproduct on $\widehat{\barB}(Y(\fg))$
  decomposes as the Drinfeld coproduct on~$\Ydg$.
\end{enumerate}
Proposition~\ref{prop:yangian-dk4-typea-frontier} verifies
(a) at finite stages via the auxiliary-kernel identity
$L_a(u) = R_{0a}(u - a)$, which is the tangent-space
computation of the moduli problem restricted to the
fundamental evaluation line
(Remark~\ref{rem:dk4-formal-moduli-vs-rtt}(ii)).

The completed bar-cobar equivalence
(Corollary~\ref{cor:completed-bar-cobar-yangian}) also sharpens
the four MC3 extension conjectures
(Conjecture~\ref{conj:mc3-formal-moduli-reformulation}):
\begin{enumerate}[label=\textup{(\roman*)}]
\item \emph{Pro-Weyl recovery}
  \textup{(}Conjecture~\ref{conj:pro-weyl-recovery}\textup{)}:
  for each rational $\ell$-weight~$\Psi$ with Drinfeld
  polynomial of degree~$d$, the Weyl module $W_m$ for
  $m \geq d$ is a module over~$\cA_{\leq m}$, and
  the transition maps $W_{m+1} \twoheadrightarrow W_m$ are
  surjective (universal highest-weight quotients).
  The completed bar-cobar equivalence transports the
  pro-Weyl system to a pro-system of bar complexes
  satisfying Mittag-Leffler, giving
  $M(\Psi) \simeq \varprojlim_m W_m$ in the completed
  factorization category.

\item \emph{DK on compacts}
  \textup{(}Conjecture~\ref{conj:dk-compacts-completion}\textup{)}:
  the Francis--Gaitsgory pro-nilpotent completion of the
  evaluation-generated core is now a quotient of the
  ind-completed category
  (Theorem~\ref{thm:ind-completed-extension}), with the
  completed bar-cobar equivalence providing the passage.
  What remains is the compact generation statement of
  Conjecture~\ref{conj:shifted-prefundamental-generation}.
\end{enumerate}
\end{remark}

\begin{definition}[Ordered \texorpdfstring{$\Eone$}{E1}-factorization category]
\label{def:ordered-e1-factorization}
\index{factorization category!ordered $\Eone$-|textbf}
For an $\Eone$-chiral algebra~$\cA$ on a curve~$X$,
the \emph{ordered $\Eone$-factorization category}
$\Factord(X;\cA)$ is the stable $\infty$-category
of $\cA$-modules on ordered configuration spaces,
with the associative chiral tensor structure induced
by the $\Eone$-operad action
(Definition~\ref{def:e1-factorization-category}).
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\end{definition}

\begin{definition}[Spectral quantum group]
\label{def:spectral-quantum-group}
\index{quantum group!spectral|textbf}
For a Koszul dual~$\cA^!$ with spectral $R$-matrix~$R_{\cA}$,
the \emph{spectral quantum group} $\QGspec(R_{\cA})$ is the
factorization quantum group whose representation category
is controlled by the spectral $R$-matrix, in the sense of
Latyntsev~\cite{Latyntsev23}.
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\end{definition}

\begin{definition}[dg-shifted Yangian]
\label{def:dg-shifted-yangian}
\index{Yangian!dg-shifted|textbf}
For a Koszul dual~$\cA^!$, the \emph{dg-shifted Yangian}
$\Ydg_{\cA}$ is the dg algebra with translation operator,
Maurer--Cartan element~$r(z)$, and twisted coproduct,
as constructed in the perturbative holomorphic-topological
setting of Costello--Yamazaki~\cite{costello-yamazaki} and
Costello--Gwilliam~\cite{CG17}.
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\end{definition}

\begin{definition}[RTT-adapted filtration on a dg-shifted Yangian]
\label{def:rtt-adapted-filtration}
Let $\Ydg_{\cA}$ be a dg-shifted Yangian.  An
\emph{RTT-adapted filtration} on $\Ydg_{\cA}$ is a descending
filtration by closed dg ideals
\[
F^1\Ydg_{\cA} \supset F^2\Ydg_{\cA} \supset \cdots
\]
such that:
\begin{enumerate}
\item $\Ydg_{\cA} \cong
  \varprojlim_N \Ydg_{\cA}/F^{N+1}\Ydg_{\cA}$ as a complete dg algebra;
\item the differential, translation operator, Maurer--Cartan element
  $r(z)$, and twisted coproduct preserve the filtration;
\item each quotient
  $\Ydg_{\cA}/F^{N+1}\Ydg_{\cA}$ is dg quasi-isomorphic to the finite
  RTT stage $Y_{\le N}$; and
\item these quotient quasi-isomorphisms are compatible with the RTT
  truncation maps and the finite-stage bar-cobar data.
\end{enumerate}
This is the exact H-level input required by
Corollary~\ref{cor:yangian-hlevel-comparison-criterion}.
\end{definition}

\begin{proposition}[Formal quotient criterion for dg-shifted Yangians;
\ClaimStatusProvedHere]
\label{prop:dg-shifted-quotient-criterion}
Let $\Ydg_{\cA}$ be a dg algebra equipped with:
\begin{enumerate}
\item a translation operator;
\item a Maurer--Cartan element $r(z)$;
\item a twisted coproduct; and
\item a descending sequence of closed dg ideals
  \[
  F^1\Ydg_{\cA} \supset F^2\Ydg_{\cA} \supset \cdots
  \]
  preserved by the differential, translation operator,
  Maurer--Cartan element, and twisted coproduct.
\end{enumerate}
Then every finite quotient
\[
\Ydg_{\cA}/F^{N+1}\Ydg_{\cA}
\]
inherits the same dg-shifted Yangian type of structure, and the quotient
maps form an inverse system of dg-shifted objects.

If, in addition, these quotients are dg quasi-isomorphic to the finite
RTT stages $Y_{\le N}$ compatibly with RTT truncation, evaluation
modules, and the degree-$2$ twisting morphism, then
Definition~\ref{def:rtt-adapted-filtration} holds and
Corollary~\ref{cor:yangian-hlevel-comparison-criterion} applies.
\end{proposition}

\begin{proof}
Preservation of the ideals by the differential descends the dg
structure to each quotient.  Preservation by the translation operator,
Maurer--Cartan element, and twisted coproduct descends those data as
well, because each operation factors through the quotient by the same
ideal.  Compatibility of the quotient maps with the preserved
operations makes the family of quotients an inverse system of
dg-shifted objects.

The additional compatibility hypotheses are exactly the remaining items
of Definition~\ref{def:rtt-adapted-filtration}.  Once they are checked,
Corollary~\ref{cor:yangian-hlevel-comparison-criterion} gives the
comparison with $\widehat Y_{\mathrm{RTT}}$.
\end{proof}

\begin{conjecture}[Full derived Drinfeld--Kohno bridge;
\ClaimStatusConjectured]
\label{conj:full-dk-bridge}
\index{Drinfeld--Kohno!full bridge|textbf}
\index{triple equivalence!factorization--Yangian--quantum group}
For affine/Yangian-type modular Koszul $\Eone$-objects~$\cA$
satisfying:
\textup{(i)}~$\Eone$-Koszulness,
\textup{(ii)}~pro-nilpotent completion/convergence,
\textup{(iii)}~existence of spectral $R$-matrix data, and
\textup{(iv)}~extension of the evaluation-locus comparison to
the full category~$\mathcal{O}$,
there are equivalences of braided monoidal stable
$\infty$-categories
\begin{equation}\label{eq:triple-equivalence}
\Factord(X;\cA)
\;\simeq\;
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\;\simeq\;
\operatorname{Rep}^{\mathrm{spec}}\!
  \bigl(\QGspec(R_{\cA})\bigr)^{\mathrm{op}},
\end{equation}
compatible with evaluation modules and KZ/KZB monodromy,
and identifying $r(z) = \tau|_{\deg 2}$ where $\tau$ is
the propagator of the $\Eone$-bar complex.

\smallskip\noindent
\emph{Status.}
Conjecture~\textup{\ref{conj:full-derived-dk}} is the DK-3 outer
factorization equivalence; Theorem~\textup{\ref{thm:factorization-dk-eval}}
proves DK-1 on the evaluation locus.  The Yangian middle term and the
triple formulation are the DK-4/DK-5 completion.
(Contributing to Conjecture~\ref{conj:master-dk-kl}.)
\end{conjecture}

\begin{proposition}[Formal reduction principle from DK-3 to
DK-4/DK-5; \ClaimStatusProvedHere]
\label{prop:yangian-dk-mc4-reduction}
Fix an affine/Yangian-type modular Koszul $\Eone$-object~$\cA$.
Assume the DK-3 outer equivalence is established on the ordered
factorization model, namely that there is a braided monoidal
equivalence
\[
\Factord(X;\cA)
\xrightarrow{\sim}
\operatorname{Rep}^{\mathrm{spec}}\!
  \bigl(\QGspec(R_{\cA})\bigr)^{\mathrm{op}}
\]
compatible with evaluation modules and extending the
evaluation-locus comparison of
Theorem~\ref{thm:factorization-dk-eval}.  Then the remaining content of
Conjecture~\ref{conj:full-dk-bridge} is exactly the construction of a
dg-shifted Yangian~$\Ydg_{\cA}$ whose RTT-adapted filtration satisfies
Corollary~\ref{cor:yangian-hlevel-comparison-criterion}, together with
the module-category enhancement
\[
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\xrightarrow{\sim}
\operatorname{Rep}^{\mathrm{spec}}\!
  \bigl(\QGspec(R_{\cA})\bigr)^{\mathrm{op}}.
\]
In particular, once DK-3 is in hand, the genuinely new Yangian input is
the MC4 H-level comparison problem and its passage from completed
dg-algebra comparison to completed module-category equivalence; it is
not a second factorization comparison on the evaluation locus.
\end{proposition}

\begin{proof}
The ordered factorization term and the right-hand spectral quantum-group
term in~\eqref{eq:triple-equivalence} are fixed by the assumed DK-3
outer equivalence, so after DK-3 the only missing part of
Conjecture~\ref{conj:full-dk-bridge} is the middle equivalence
\[
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\simeq
\operatorname{Rep}^{\mathrm{spec}}\!
  \bigl(\QGspec(R_{\cA})\bigr)^{\mathrm{op}}.
\]
Corollary~\ref{cor:yangian-hlevel-comparison-criterion} shows that, once
$\Ydg_{\cA}$ carries a separated complete RTT-adapted filtration with
the theorematic finite RTT quotients, the underlying completed dg
algebra comparison with the standard RTT completion becomes formal.
Thus the remaining mathematical content is precisely the MC4
construction of that filtered H-level target together with the passage
from the dg comparison to the completed module-category equivalence
displayed above.  This is exactly the DK-4/DK-5 remainder.
\end{proof}

\begin{proposition}[DK-4 reduction to the fundamental residue packet in
standard type~A; \ClaimStatusProvedHere]
\label{prop:yangian-dk4-typea-frontier}
Assume the hypotheses of
Proposition~\ref{prop:yangian-dk-mc4-reduction} and work with the
standard type-A RTT tower.  Then the remaining DK-4 input is reduced to
the boundary-strip identities
\[
\Delta_{a,0}(N)=0
\qquad (0\le a\le N,\ N\ge 0)
\]
for the defects
\[
\Delta_{a,0}(N)
=\mathsf{K}^{\mathrm{line}}_{a,0}(N)
-\mathsf{K}^{\mathrm{RTT}}_{a,0}(N),
\]
together with the standard twisted-coproduct multiplication law on
fundamental evaluation modules.  Equivalently, for the standard type-A
tower it is enough to prove the pairwise auxiliary-kernel identity
\[
L_a(u)=R_{0a}(u-a)
\]
on the fundamental evaluation line.

If, moreover, the one-factor line operator is functorial for the
diagonal $\mathfrak{sl}_M$-action and normalized by
$L_a(u)\to 1$ as $u\to\infty$, then the same DK-4 input is further
reduced to transport of the standard residue formula
\[
\operatorname*{Res}_{u=a}L_a(u)=-\hbar P.
\]
For $M\ge 2$, this transport statement is further reduced to the
ordered mixed-tensor
identity
\[
\Xi_a(e_1\otimes e_2)=-\hbar(e_2\otimes e_1).
\]

By
Proposition~\ref{prop:dg-shifted-rtt-typea-uniform-single-line},
this single ordered tensor-line computation already determines the full
residue operator $\Xi_a=-\hbar P$ uniformly in the rank.
Proposition~\ref{prop:dg-shifted-rtt-standard-typea-local-packet}
shows that this residue formula already holds on the theorematic
standard RTT tower itself.  Thus the genuinely live local input is to
identify the dg-shifted or factorization one-factor kernel with that
standard normalized residue, equivalently with the same mixed-tensor
matrix coefficient on the fundamental line.

Under one-loop exactness,
Proposition~\ref{prop:dg-shifted-rtt-degree2-mixed-tensor-criterion}
reduces this transport problem further to the ordered mixed-tensor
coefficient of the degree-$2$ twisting morphism $r(z)=\tau|_{\deg 2}$.
Corollary~\ref{cor:dg-shifted-rtt-seed-normalized-coefficient}
shows that, in the standard logarithmic normalization, this is
equivalently the ordered mixed-tensor coefficient of the operator
$r_a^{\mathrm{fund}}(z)$ itself.

Proposition~\ref{prop:dg-shifted-rtt-degree2-scalar-normalization}
then removes the remaining one-loop matrix ambiguity: after
degree-$2$ scalar normalization, the only genuinely live datum is the
scalar coefficient of the permutation operator.  In particular,
Corollary~\ref{cor:dg-shifted-rtt-degree2-casimir-normalization}
shows that the trace-zero convention
$P-\frac{1}{M}\id$ reduces to the same scalar packet, and
Proposition~\ref{prop:dg-shifted-rtt-degree2-fundamental-casimir}
computes that scalar as $-1$ once the standard fundamental Casimir
insertion is identified.
Corollary~\ref{cor:factorization-fundamental-casimir-identity} proves
that the factorization side already satisfies this identity, and
Proposition~\ref{prop:dg-shifted-factorization-shared-seed} shows that
any dg-shifted realization presented by the same ordered bar seed
inherits the same coefficient.  Thus the genuinely live local step is
no longer a new coefficient computation, but the realization of the
dg-shifted target with that shared bar seed.

Thus, after DK-3, the genuinely analytic Yangian frontier on the
standard type-A tower is the H-level dg-shifted realization and the
compact-core DK-5 packet, not a new residue computation inside the
standard RTT tower.
\end{proposition}

\begin{proof}
By Proposition~\ref{prop:yangian-dk-mc4-reduction}, once DK-3 is fixed
the remaining work is to construct a dg-shifted Yangian with an
RTT-adapted filtration satisfying
Corollary~\ref{cor:yangian-hlevel-comparison-criterion}.  The finite
quotient comparison required there is reduced by
Proposition~\ref{prop:dg-shifted-rtt-oneloop-kernel-criterion} to the
coefficient identities
$\mathsf{K}^{\mathrm{line}}_{a,b}(N)
=\mathsf{K}^{\mathrm{RTT}}_{a,b}(N)$,
by Proposition~\ref{prop:dg-shifted-rtt-boundary-seed} to the boundary
strip $\Delta_{a,0}(N)$, and by
Proposition~\ref{prop:dg-shifted-rtt-fundamental-propagation} to the
fundamental evaluation family together with the standard
twisted-coproduct multiplication law.

Proposition~\ref{prop:dg-shifted-rtt-auxiliary-kernel-criterion} then
reduces this boundary-strip packet to the pairwise kernel identity
$L_a(u)=R_{0a}(u-a)$ on the fundamental line.  Under the symmetry and
normalization hypotheses,
Corollary~\ref{cor:dg-shifted-rtt-typea-residue-reduction} reduces that
identity to the residue formula
$\operatorname*{Res}_{u=a}L_a(u)=-\hbar P$, and
Corollary~\ref{cor:dg-shifted-rtt-typea-single-line} reduces the
transport-normalized residue formula further to the ordered
mixed-tensor check displayed in
the statement, while
Proposition~\ref{prop:dg-shifted-rtt-typea-uniform-single-line}
shows that this one check already determines the whole residue
operator uniformly in~$M$.  Proposition~\ref{prop:dg-shifted-rtt-standard-typea-local-packet}
then identifies that residue explicitly on the theorematic standard
RTT side.
\end{proof}

\begin{proposition}[DK-5 reduction to compact-generator comparison;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-compact-generators}
Assume the hypotheses of
Proposition~\ref{prop:yangian-dk4-typea-frontier}.  Let
\[
\mathcal{G}^{\mathrm{fund}}_{Y}
\subset \operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA}),
\qquad
\mathcal{G}^{\mathrm{fund}}_{q}
\subset \operatorname{Rep}^{\mathrm{spec}}\!
  \bigl(\QGspec(R_{\cA})\bigr)^{\mathrm{op}}
\]
be the full subcategories generated by the completed images of finite
ordered tensor products of fundamental evaluation modules.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item both ambient stable categories are compactly generated, and
  their compact objects are the thick idempotent-complete closures of
  $\mathcal{G}^{\mathrm{fund}}_{Y}$ and
  $\mathcal{G}^{\mathrm{fund}}_{q}$, respectively;
\item the DK-4 comparison supplies an exact colimit-preserving functor
  \[
  F_{\mathrm{comp}}\colon
  \operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
  \longrightarrow
  \operatorname{Rep}^{\mathrm{spec}}\!
    \bigl(\QGspec(R_{\cA})\bigr)^{\mathrm{op}}
  \]
  compatible with the dg comparison
  $\Ydg_{\cA}\xrightarrow{\sim}\widehat Y_{\mathrm{RTT}}$ and with the
  DK-3 transport on the evaluation-generated packet; and
\item the restriction of $F_{\mathrm{comp}}$ to
  $\mathcal{G}^{\mathrm{fund}}_{Y}$ is an equivalence onto
  $\mathcal{G}^{\mathrm{fund}}_{q}$.
\end{enumerate}
Then $F_{\mathrm{comp}}$ is an equivalence of stable categories.  In
particular, after DK-4 the remaining DK-5 input is the compact-generator
comparison on the completed module categories; the passage from that
packet to the full completed equivalence is formal.
\end{proposition}

\begin{proof}
By assumption~\textup{(iii)}, the functor
$F_{\mathrm{comp}}$ is an equivalence on the chosen generator packet.
Because $F_{\mathrm{comp}}$ is exact, it preserves shifts, cones, and
direct summands, so it is an equivalence on the thick idempotent-complete
closures of that packet.  Assumption~\textup{(i)} identifies those
closures with the compact objects in the two ambient categories.

Now both categories are compactly generated, and
$F_{\mathrm{comp}}$ preserves colimits by assumption~\textup{(ii)}.
Hence the same uniqueness-of-extension mechanism used in the proof of
Theorem~\ref{thm:chiral-co-contra-correspondence} applies: an exact
colimit-preserving functor between compactly generated stable
categories is determined by its restriction to compact generators, and
an equivalence on those generators extends to an equivalence on the
whole categories.  Therefore $F_{\mathrm{comp}}$ is an equivalence.
\end{proof}

\begin{proposition}[Compact-core comparison reduces to the completed
fundamental packet; \ClaimStatusProvedHere]
\label{prop:yangian-dk5-fundamental-packet}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-compact-generators}.  Write
\[
\mathcal{C}_Y^\omega
:=
\operatorname{thick}^{\mathrm{idemp}}
\bigl(\mathcal{G}^{\mathrm{fund}}_{Y}\bigr),
\qquad
\mathcal{C}_q^\omega
:=
\operatorname{thick}^{\mathrm{idemp}}
\bigl(\mathcal{G}^{\mathrm{fund}}_{q}\bigr)
\]
for the compact cores of the two completed categories, and let
\[
\mathcal{P}^{\mathrm{fund}}_{Y}\subset \mathcal{C}_Y^\omega,
\qquad
\mathcal{P}^{\mathrm{fund}}_{q}\subset \mathcal{C}_q^\omega
\]
be the full subcategories spanned by the completed fundamental
evaluation modules themselves.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item each compact core is the smallest full stable
  idempotent-complete braided monoidal subcategory containing its
  completed fundamental packet;
\item there exist exact braided monoidal functors
  \[
  KZ^\omega_{\mathrm{comp}}\colon
  \mathcal{C}_Y^\omega \to \mathcal{C}_q^\omega,
  \qquad
  LZ^\omega_{\mathrm{comp}}\colon
  \mathcal{C}_q^\omega \to \mathcal{C}_Y^\omega;
  \]
\item the restrictions of these functors to
  $\mathcal{P}^{\mathrm{fund}}_{Y}$ and
  $\mathcal{P}^{\mathrm{fund}}_{q}$ recover the DK-3 transport on the
  completed fundamental evaluation packet; and
\item both composites
  \[
  LZ^\omega_{\mathrm{comp}} \circ KZ^\omega_{\mathrm{comp}},
  \qquad
  KZ^\omega_{\mathrm{comp}} \circ LZ^\omega_{\mathrm{comp}}
  \]
  are naturally isomorphic to the identity on the completed
  fundamental packets.
\end{enumerate}
Then the two functors are quasi-inverse exact braided monoidal
equivalences
\[
KZ^\omega_{\mathrm{comp}}\colon
\mathcal{C}_Y^\omega \xrightarrow{\sim} \mathcal{C}_q^\omega,
\qquad
LZ^\omega_{\mathrm{comp}}\colon
\mathcal{C}_q^\omega \xrightarrow{\sim} \mathcal{C}_Y^\omega.
\]

Equivalently, once the compact cores are generated by completed
fundamental evaluation modules, the compact-core DK-5 packet is forced
by transport on that completed fundamental packet.
\end{proposition}

\begin{proof}
This is the compact-core analogue of
Proposition~\ref{prop:yangian-dk3-generated-core}.  By
assumption~\textup{(i)}, each compact core is obtained from its
completed fundamental packet by finite iterates of shifts, cones,
direct summands, and ordered tensor products.  Exact braided monoidal
functors preserve each of these operations.  Therefore any natural
transformation between exact braided monoidal functors that is an
isomorphism on the completed fundamental packet remains an isomorphism
on the full compact core.

Apply this to the two composites in assumption~\textup{(iv)}.  Since
they are naturally isomorphic to the identity on the completed
fundamental packets, they are naturally isomorphic to the identity on
$\mathcal{C}_Y^\omega$ and $\mathcal{C}_q^\omega$.  Hence
$KZ^\omega_{\mathrm{comp}}$ and $LZ^\omega_{\mathrm{comp}}$ are
quasi-inverse exact braided monoidal equivalences.
\end{proof}

\begin{proposition}[DK-5 comparison functor is the ind-extension of the
compact core; \ClaimStatusProvedHere]
\label{prop:yangian-dk5-ind-extension}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-compact-generators}.  Write
\[
\mathcal{C}_Y^\omega
:=
\operatorname{thick}^{\mathrm{idemp}}
\bigl(\mathcal{G}^{\mathrm{fund}}_{Y}\bigr),
\qquad
\mathcal{C}_q^\omega
:=
\operatorname{thick}^{\mathrm{idemp}}
\bigl(\mathcal{G}^{\mathrm{fund}}_{q}\bigr)
\]
for the compact cores of the two completed categories.  Assume:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the ambient categories
  $\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})$ and
  $\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}$
  are presentable, stable, and compactly generated, with compact
  objects exactly $\mathcal{C}_Y^\omega$ and $\mathcal{C}_q^\omega$;
\item there is an exact equivalence
  \[
  F^\omega\colon \mathcal{C}_Y^\omega \xrightarrow{\sim} \mathcal{C}_q^\omega
  \]
  whose restriction to the completed fundamental evaluation packet
  agrees with the DK-3 transport on the evaluation-generated core.
\end{enumerate}
Then there exists a unique exact colimit-preserving equivalence
\[
\operatorname{Ind}(F^\omega)\colon
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\xrightarrow{\sim}
\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}
\]
extending $F^\omega$.

In particular, once the compact-core equivalence is constructed, the
comparison functor appearing in
Proposition~\ref{prop:yangian-dk5-compact-generators} and its
compatibility with DK-3 on the compact generator packet are formal.
\end{proposition}

\begin{proof}
By assumption~\textup{(i)}, each ambient category is the
ind-completion of its compact objects:
\[
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\simeq
\operatorname{Ind}(\mathcal{C}_Y^\omega),
\qquad
\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}
\simeq
\operatorname{Ind}(\mathcal{C}_q^\omega).
\]
This is the same compact-generation mechanism used in
Theorem~\ref{thm:ind-completed-extension}: a presentable stable
compactly generated category is recovered from its compact part by
ind-completion.

Now apply the universal property of ind-completion to the exact
equivalence $F^\omega$.  It extends uniquely to an exact
colimit-preserving functor
\[
\operatorname{Ind}(F^\omega)\colon
\operatorname{Ind}(\mathcal{C}_Y^\omega)
\longrightarrow
\operatorname{Ind}(\mathcal{C}_q^\omega),
\]
and because $F^\omega$ is already an equivalence, its ind-extension is
an equivalence as well.  Transporting along the displayed
identifications of the ambient categories yields the claimed functor.

The final sentence is immediate: once the compact-core equivalence is
fixed, the completed comparison functor is forced to be this unique
ind-extension, so no separate completed-level functor construction
remains.
\end{proof}

\begin{corollary}[DK-5 reduces to the compact-core equivalence;
\ClaimStatusProvedHere]
\label{cor:yangian-dk5-compact-core}
Assume the hypotheses of
Corollary~\ref{cor:yangian-typea-dg-local-closure}.  Assume moreover
that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the completed dg-shifted and spectral categories are presentable,
  stable, and compactly generated;
\item their compact objects are the thick idempotent-complete closures
  of the completed fundamental evaluation packets; and
\item those compact cores are exactly equivalent in a way compatible
  with DK-3 on the completed fundamental packet.
\end{enumerate}
Then the standard type-$A$ Yangian DK-5 packet closes.

Equivalently, after the local dg-shifted packet is closed, the
remaining DK-5 input is exactly the compact-core equivalence; the
completed comparison functor itself is formal.
\end{corollary}

\begin{proof}
Under
Corollary~\ref{cor:yangian-typea-dg-local-closure}, the local DK-4
packet is already closed, so only DK-5 remains.  Assumptions
\textup{(i)}--\textup{(iii)} are precisely the hypotheses of
Proposition~\ref{prop:yangian-dk5-ind-extension}, which produces the
unique exact colimit-preserving equivalence between the completed
categories.  This is exactly the DK-5 conclusion.
\end{proof}

\begin{corollary}[DK-5 reduces to compact generation plus completed
fundamental-packet transport; \ClaimStatusProvedHere]
\label{cor:yangian-dk5-fundamental-packet}
Assume the hypotheses of
Corollary~\ref{cor:yangian-typea-dg-local-closure}.  Assume moreover
that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the completed dg-shifted and spectral categories are presentable,
  stable, and compactly generated;
\item their compact objects are the smallest full stable
  idempotent-complete braided monoidal subcategories containing the
  completed fundamental evaluation packets; and
\item there exist exact braided monoidal functors between those compact
  cores whose restrictions to the completed fundamental evaluation
  packets recover the DK-3 transport and whose composites are the
  identity on that packet.
\end{enumerate}
Then the standard type-$A$ Yangian DK-5 packet closes.

Equivalently, once the local dg-shifted packet is closed, the remaining
categorical input is compact generation together with transport on the
completed fundamental evaluation packet; the compact-core equivalence
and the ambient completed comparison functor are then formal.
\end{corollary}

\begin{proof}
Assumption~\textup{(ii)} identifies the compact objects with the
compact cores appearing in
Proposition~\ref{prop:yangian-dk5-fundamental-packet}.  By
assumption~\textup{(iii)}, that proposition yields an exact
equivalence between the compact cores.  Now apply
Proposition~\ref{prop:yangian-dk5-ind-extension} to extend that
compact-core equivalence uniquely to an exact colimit-preserving
equivalence of the ambient completed categories.  This is exactly the
DK-5 conclusion.
\end{proof}

\begin{proposition}[Compact-core DK-5 functors from realization of the
proved finite-dimensional factorization DK core; \ClaimStatusProvedHere]
\label{prop:yangian-dk5-core-realization}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-fundamental-packet}.  Let
\[
KZ_{\mathrm{fd}}\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\xrightarrow{\sim}
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
\[
LZ_{\mathrm{fd}}\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\xrightarrow{\sim}
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\]
be quasi-inverse exact braided monoidal equivalences furnished by
Theorem~\ref{thm:dk-fd-typeA}.  Assume there exist exact braided
monoidal equivalences
\[
\quad
J_Y^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\xrightarrow{\sim}
\mathcal{C}_Y^\omega,
\qquad
J_q^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\xrightarrow{\sim}
\mathcal{C}_q^\omega
\]
whose restrictions to the evaluation generators identify them with the
completed fundamental evaluation packets
$\mathcal{P}^{\mathrm{fund}}_{Y}$ and
$\mathcal{P}^{\mathrm{fund}}_{q}$.
Then
\[
KZ^\omega_{\mathrm{comp}}
:=
J_q^\omega \circ KZ_{\mathrm{fd}} \circ (J_Y^\omega)^{-1},
\qquad
LZ^\omega_{\mathrm{comp}}
:=
J_Y^\omega \circ LZ_{\mathrm{fd}} \circ (J_q^\omega)^{-1}
\]
are quasi-inverse exact braided monoidal equivalences
\[
\mathcal{C}_Y^\omega \xrightarrow{\sim} \mathcal{C}_q^\omega
\]
whose restrictions to the completed fundamental evaluation packets
recover the DK-3 transport.  In particular, the packet hypotheses of
Proposition~\ref{prop:yangian-dk5-fundamental-packet} are automatic.
\end{proposition}

\begin{proof}
The displayed functors are composites of exact braided monoidal
equivalences, hence are themselves exact braided monoidal
equivalences.  Because the completion equivalences
$J_Y^\omega$ and $J_q^\omega$ identify the evaluation generators with
the completed fundamental evaluation packets, the restrictions of
$KZ^\omega_{\mathrm{comp}}$ and $LZ^\omega_{\mathrm{comp}}$ to those
packets are exactly the DK-3 transport and its inverse.  Therefore the
composites are the identity on the completed fundamental packets, and
the final sentence follows immediately.
\end{proof}

\begin{lemma}[Finite-dimensional Yangian factorization core is
generated by fundamental evaluation objects; \ClaimStatusProvedHere]
\label{lem:yangian-fd-fundamental-generation}
For $\mathfrak{sl}_M$, the braided monoidal stable category
\[
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\]
is the smallest full stable idempotent-complete braided monoidal
subcategory containing the fundamental evaluation objects.
\end{lemma}

\begin{proof}
By Proposition~\ref{prop:dk2-thick-generation-typeA}, every
finite-dimensional irreducible Yangian module is a subquotient of a
tensor product of fundamental evaluation modules.  Applying
Lemma~\ref{lem:composition-thick-generation} to the abelian category of
finite-dimensional Yangian modules shows that the bounded derived
category is the thick triangulated closure of those fundamental
evaluation modules.  The factorization category
\[
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\]
is this same finite-dimensional stable category equipped with the
ordered factorization tensor product, and ordered tensor products of
fundamental evaluation objects remain inside the same closure.
Therefore the smallest full stable idempotent-complete braided
monoidal subcategory containing the fundamental evaluation objects is
the whole finite-dimensional Yangian factorization category.
\end{proof}

\begin{lemma}[Finite-dimensional quantum-group factorization core is
generated by fundamental evaluation objects; \ClaimStatusProvedHere]
\label{lem:quantum-fd-fundamental-generation}
For $\mathfrak{sl}_M$, the braided monoidal stable category
\[
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
is the smallest full stable idempotent-complete braided monoidal
subcategory containing the fundamental evaluation objects.
\end{lemma}

\begin{proof}
By Proposition~\ref{prop:dk2-thick-generation-typeA}, every
finite-dimensional irreducible Yangian module is a subquotient of a
tensor product of fundamental evaluation modules.  The proof of
Theorem~\ref{thm:dk-fd-typeA} upgrades that generation statement to the
factorization setting: the exact braided monoidal equivalence
\[
KZ_{\barB}\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\xrightarrow{\sim}
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
sends fundamental evaluation objects to fundamental evaluation
objects, preserves shifts, cones, direct summands, and ordered tensor
products, and is essentially surjective.  Therefore the same smallest
full stable idempotent-complete braided monoidal subcategory generated
by fundamental evaluations on the Yangian side transports to the full
finite-dimensional quantum-group factorization category.
\end{proof}

\begin{proposition}[Spectral compact-core realization is formal from
generator transport; \ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-realization-formal}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-fundamental-packet}.  Assume
\[
\mathcal{C}_q^\omega
=
\operatorname{thick}^{\mathrm{idemp}}(\mathcal{G}^{\mathrm{fund}}_{q})
\]
is the smallest full stable idempotent-complete braided monoidal
subcategory containing the completed fundamental evaluation packet.
Let
\[
\mathcal{G}^{\mathrm{fund,fd}}_{q}
\subset
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
be the full subcategory generated by finite ordered tensor products of
fundamental evaluation objects, and let
\[
J_q^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\longrightarrow
\mathcal{C}_q^\omega
\]
be an exact braided monoidal functor whose restriction
\[
\mathcal{G}^{\mathrm{fund,fd}}_{q}
\longrightarrow
\mathcal{G}^{\mathrm{fund}}_{q}
\]
is an equivalence onto the completed generator packet.  Then
\(J_q^\omega\) is an exact braided monoidal equivalence.

Equivalently, on the spectral side no additional comparison on the full
compact core remains once the generator-level completion transport is
constructed.
\end{proposition}

\begin{proof}
By Lemma~\ref{lem:quantum-fd-fundamental-generation}, the source is the
smallest full stable idempotent-complete braided monoidal subcategory
containing the fundamental evaluation objects.  By hypothesis, the
target enjoys the same generation property for the completed
fundamental packet.  Because \(J_q^\omega\) is exact and braided
monoidal, it preserves shifts, cones, direct summands, and ordered
tensor products.  Since its restriction to
\(\mathcal{G}^{\mathrm{fund,fd}}_{q}\) is already an equivalence onto
\(\mathcal{G}^{\mathrm{fund}}_{q}\), the same thick-closure argument as
in Proposition~\ref{prop:yangian-dk5-compact-generators} upgrades that
equivalence on the generator packet to an equivalence on the thick
idempotent-complete closures.  Those closures are exactly the source
and target by Lemma~\ref{lem:quantum-fd-fundamental-generation} and the
displayed hypothesis on \(\mathcal{C}_q^\omega\).  Thus \(J_q^\omega\)
is an exact braided monoidal equivalence.
\end{proof}

\begin{proposition}[On the spectral side, ordered tensor-generator
transport is forced by the completed fundamental packet;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-fundamental-packet}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-spectral-realization-formal}.  Let
\[
\mathcal{P}^{\mathrm{fund,fd}}_{q}
\subset
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
be the full subcategory spanned by the fundamental evaluation objects
themselves, and let
\[
\mathcal{P}^{\mathrm{fund}}_{q}
\subset
\mathcal{C}_q^\omega
\]
be the full subcategory spanned by their completed spectral images.
Assume that the exact braided monoidal functor
\[
J_q^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\longrightarrow
\mathcal{C}_q^\omega
\]
restricts to an equivalence
\[
\mathcal{P}^{\mathrm{fund,fd}}_{q}
\xrightarrow{\sim}
\mathcal{P}^{\mathrm{fund}}_{q}.
\]
Then its restriction
\[
\mathcal{G}^{\mathrm{fund,fd}}_{q}
\longrightarrow
\mathcal{G}^{\mathrm{fund}}_{q}
\]
is automatically an equivalence onto the completed spectral
generator packet.  Consequently, the hypotheses of
Proposition~\ref{prop:yangian-dk5-spectral-realization-formal} are
already satisfied, so \(J_q^\omega\) is an exact braided monoidal
equivalence.

Equivalently, on the spectral side the genuinely non-formal packet is
not the whole ordered tensor-generator family: it is enough to place
the individual fundamental evaluation objects inside the completed
spectral category in an exact braided-monoidal way.
\end{proposition}

\begin{proof}
By Lemma~\ref{lem:quantum-fd-fundamental-generation}, the source
\[
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
is the smallest full stable idempotent-complete braided monoidal
subcategory containing \(\mathcal{P}^{\mathrm{fund,fd}}_{q}\).  By the
standing hypothesis of
Proposition~\ref{prop:yangian-dk5-spectral-realization-formal}, the
target \(\mathcal{C}_q^\omega\) enjoys the same generation property for
\(\mathcal{P}^{\mathrm{fund}}_{q}\).  Because \(J_q^\omega\) is exact
and braided monoidal, it preserves shifts, cones, direct summands, and
ordered tensor products.  Since its restriction to
\(\mathcal{P}^{\mathrm{fund,fd}}_{q}\) is already an equivalence onto
\(\mathcal{P}^{\mathrm{fund}}_{q}\), the same thick-closure argument as
in Proposition~\ref{prop:yangian-dk5-dg-realization-formal} upgrades
that equivalence on the completed fundamental packet to an exact
braided monoidal equivalence on the full finite-dimensional spectral
core.

In particular, the restriction of \(J_q^\omega\) to
\(\mathcal{G}^{\mathrm{fund,fd}}_{q}\) is an equivalence onto
\(\mathcal{G}^{\mathrm{fund}}_{q}\), since those packets are the full
subcategories generated by finite ordered tensor products of the same
fundamental objects on the source and target sides.  Therefore the
generator-packet hypothesis of
Proposition~\ref{prop:yangian-dk5-spectral-realization-formal} is
automatic.  The final sentence follows.
\end{proof}

\begin{lemma}[Type-\texorpdfstring{$A$}{A} quantum-group fundamental packet is generated
by the vector evaluation line; \ClaimStatusProvedHere]
\label{lem:quantum-fd-vector-fundamental-generation}
Let
\[
\mathcal{P}^{\mathrm{vec,fd}}_{q}
\subset
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
be the full subcategory spanned by the vector evaluation objects.
Then every fundamental evaluation object of
\(\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}\)
belongs to the smallest full stable idempotent-complete braided
monoidal subcategory containing
\(\mathcal{P}^{\mathrm{vec,fd}}_{q}\).

Equivalently, on the finite-dimensional spectral side the full
fundamental packet is generated by the vector evaluation line.
\end{lemma}

\begin{proof}
Each type-$A$ fundamental Kirillov--Reshetikhin module is the image of
the $q$-antisymmetrizer on an ordered tensor power of vector
evaluation modules (\cite[Ch.~12]{ChariPressley94},
\cite[\S2]{Hernandez05}), hence a direct summand.  The closure
property follows.
\end{proof}

\begin{proposition}[On the spectral side, the completed fundamental
packet is forced by the completed vector packet;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-vector-packet}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-spectral-fundamental-packet}.  Let
\[
\mathcal{P}^{\mathrm{vec,fd}}_{q}
\subset
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\]
be the full subcategory generated by finite ordered tensor products of
the vector evaluation objects, and
let
\[
\mathcal{P}^{\mathrm{vec}}_{q}
\subset
\mathcal{C}_q^\omega
\]
be the full subcategory generated by the corresponding completed
spectral tensor packet.
Assume that the exact braided monoidal functor
\[
J_q^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\longrightarrow
\mathcal{C}_q^\omega
\]
restricts to an equivalence
\[
\mathcal{P}^{\mathrm{vec,fd}}_{q}
\xrightarrow{\sim}
\mathcal{P}^{\mathrm{vec}}_{q}.
\]
Let
\[
\mathcal{P}^{\mathrm{fund}}_{q}
\subset
\mathcal{C}_q^\omega
\]
be the full subcategory spanned by the standard type-$A$
$q$-antisymmetric direct summands inside finite ordered tensor powers
of \(\mathcal{P}^{\mathrm{vec}}_{q}\), equivalently by the completed
spectral images of the source fundamental evaluation objects.  Then
\(J_q^\omega\) restricts to an equivalence
\[
\mathcal{P}^{\mathrm{fund,fd}}_{q}
\xrightarrow{\sim}
\mathcal{P}^{\mathrm{fund}}_{q}.
\]
Consequently the hypotheses of
Proposition~\ref{prop:yangian-dk5-spectral-fundamental-packet} are
already satisfied, so \(J_q^\omega\) is an exact braided monoidal
equivalence.

\end{proposition}

\begin{proof}
By Lemma~\ref{lem:quantum-fd-vector-fundamental-generation}, every
source fundamental evaluation object is a $q$-antisymmetrizer summand
of an ordered tensor power of vector evaluation objects.  Since
\(J_q^\omega\) is exact and braided monoidal, it preserves these
summands, giving the equivalence on
\(\mathcal{P}^{\mathrm{fund,fd}}_{q}\).  Now apply
Proposition~\ref{prop:yangian-dk5-spectral-fundamental-packet}.
\end{proof}

\begin{proposition}[On the spectral side, ordered vector-packet
transport is forced by the completed vector line;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-vector-line}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-spectral-vector-packet}.  Let
\(\mathcal{L}^{\mathrm{vec,fd}}_{q}\) and
\(\mathcal{L}^{\mathrm{vec}}_{q}\) be the full subcategories
spanned by the vector evaluation objects and their completed spectral
images, respectively.
Assume that \(J_q^\omega\)
restricts to an equivalence
\[
\mathcal{L}^{\mathrm{vec,fd}}_{q}
\xrightarrow{\sim}
\mathcal{L}^{\mathrm{vec}}_{q}.
\]
Then on every object of \(\mathcal{P}^{\mathrm{vec,fd}}_{q}\) the
restriction of \(J_q^\omega\) is forced to be the ordered tensor
product of the corresponding completed vector objects, and on the
braid-group operators of the ordered vector packet it is forced to be
the trigonometric braiding of \(\mathcal{C}_q^\omega\)
(once the completed spectral vector line is fixed,
the transport on the whole ordered vector packet carries no additional freedom).
\end{proposition}

\begin{proof}
Since \(\mathcal{P}^{\mathrm{vec,fd}}_{q}\) consists of finite ordered
tensor products of objects of \(\mathcal{L}^{\mathrm{vec,fd}}_{q}\),
braided monoidality of \(J_q^\omega\) forces both the object-level and
braiding-level transport.
\end{proof}

\begin{proposition}[Standard quantum-loop vector seed and additive
log-spectral shifts; \ClaimStatusProvedHere]
\label{prop:quantum-fd-vector-seed-shifts}
Let
\[
V(0)\in \mathcal{L}^{\mathrm{vec,fd}}_{q}
\]
be the vector evaluation object of the quantum loop algebra at
multiplicative spectral parameter \(1\), viewed on the additive
log-spectral line via the exponential coordinate \(z=e^u\).  For every
\(a\in \mathbb{C}\), let
\[
\mathsf{T}^{\mathrm{fd}}_a\colon
\mathcal{L}^{\mathrm{vec,fd}}_{q}\xrightarrow{\sim}
\mathcal{L}^{\mathrm{vec,fd}}_{q}
\]
be the pullback along the loop-rotation automorphism \(z\mapsto e^a z\)
of the quantum loop algebra.  Then each
\(\mathsf{T}^{\mathrm{fd}}_a\) is an exact braided-monoidal
autoequivalence, and
\[
\mathsf{T}^{\mathrm{fd}}_a(V(0))\cong V(a),
\qquad
\mathsf{T}^{\mathrm{fd}}_{a+b}\cong
\mathsf{T}^{\mathrm{fd}}_a\circ \mathsf{T}^{\mathrm{fd}}_b,
\qquad
\mathsf{T}^{\mathrm{fd}}_0\cong \id .
\]

\end{proposition}

\begin{proof}
Loop rotation \(z\mapsto e^a z\) is a Hopf algebra automorphism of the
quantum loop algebra (\cite[Ch.~12]{ChariPressley94},
\cite[\S2]{Hernandez05}), so pullback defines exact braided-monoidal
autoequivalences.  The group law and unit follow from composition.
\end{proof}

\begin{lemma}[Quantum-loop vector seed is Schur-simple;
\ClaimStatusProvedHere]
\label{lem:quantum-fd-vector-seed-schur}
For every \(a\in\mathbb C\), the type-$A$ vector evaluation object
\(V(a)\in \operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}\)
is simple, so \(\End(V(a))\cong \mathbb C\).
\end{lemma}

\begin{proof}
The vector evaluation object is the first fundamental
Kirillov--Reshetikhin module, hence simple (\cite[Ch.~12]{ChariPressley94}).
Schur's lemma gives \(\End(V(a))\cong\mathbb C\).
\end{proof}

\begin{proposition}[On the spectral side, the completed vector line is
forced by one completed vector seed together with spectral shifts;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-vector-seed}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-spectral-vector-line}.  Fix one
source vector evaluation object \(V(0)\in
\mathcal{L}^{\mathrm{vec,fd}}_{q}\) and one completed spectral vector
object \(V^\omega(0)\in \mathcal{L}^{\mathrm{vec}}_{q}\).  Assume
moreover that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item for every \(a\in \mathbb{C}\), the source vector evaluation line
  carries an exact braided-monoidal spectral-shift autoequivalence
  \[
  \mathsf{T}^{\mathrm{fd}}_a\colon
  \mathcal{L}^{\mathrm{vec,fd}}_{q}\xrightarrow{\sim}
  \mathcal{L}^{\mathrm{vec,fd}}_{q}
  \]
  with \(\mathsf{T}^{\mathrm{fd}}_a(V(0))\cong V(a)\);
\item for every \(a\in \mathbb{C}\), the completed spectral vector line
  carries an exact braided-monoidal spectral-shift autoequivalence
  \[
  \mathsf{T}^{\omega}_a\colon
  \mathcal{L}^{\mathrm{vec}}_{q}\xrightarrow{\sim}
  \mathcal{L}^{\mathrm{vec}}_{q}
  \]
  with \(\mathsf{T}^{\omega}_a(V^\omega(0))\cong V^\omega(a)\); and
\item the exact braided monoidal functor \(J_q^\omega\) intertwines
  these shift autoequivalences on the vector line:
  \[
  J_q^\omega\circ \mathsf{T}^{\mathrm{fd}}_a
  \cong
  \mathsf{T}^{\omega}_a\circ J_q^\omega
  \qquad (a\in \mathbb{C}),
  \]
  and identifies \(V(0)\) with \(V^\omega(0)\).
\end{enumerate}
Then the restriction of \(J_q^\omega\) to
\(\mathcal{L}^{\mathrm{vec,fd}}_{q}\) is uniquely determined up to
unique natural isomorphism by the image of the single seed object
\(V(0)\) together with the compatible spectral-shift structure.
\end{proposition}

\begin{proof}
The intertwining relation~\textup{(iii)} forces \(J_q^\omega(V(a))
\cong V^\omega(a)\) for every \(a\), since every object of
\(\mathcal{L}^{\mathrm{vec,fd}}_{q}\) is obtained from the seed by
the shift autoequivalences~\textup{(i)}--\textup{(ii)}.
\end{proof}

\begin{proposition}[On the realized spectral vector-line locus, the
completed vector seed and spectral shifts are canonical;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-seed-shift-construction}
Work in the setting of
Propositions~\ref{prop:quantum-fd-vector-seed-shifts}
and~\ref{prop:yangian-dk5-spectral-vector-line}.  Assume that the exact
braided monoidal functor
\[
J_q^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\longrightarrow
\mathcal{C}_q^\omega
\]
restricts to an equivalence
\[
\mathcal{L}^{\mathrm{vec,fd}}_{q}\xrightarrow{\sim}
\mathcal{L}^{\mathrm{vec}}_{q}.
\]
Define
\[
V^\omega(0):=J_q^\omega(V(0))
\]
and for each \(a\in\mathbb{C}\) define
\[
\mathsf{T}^{\omega}_a
:=
\left.J_q^\omega\right|_{\mathcal{L}^{\mathrm{vec,fd}}_{q}}
\circ
\mathsf{T}^{\mathrm{fd}}_a
\circ
\left(\left.J_q^\omega\right|_{\mathcal{L}^{\mathrm{vec,fd}}_{q}}\right)^{-1}.
\]
Then each \(\mathsf{T}^{\omega}_a\) is an exact braided-monoidal
autoequivalence of \(\mathcal{L}^{\mathrm{vec}}_{q}\), and
\[
\mathsf{T}^{\omega}_a(V^\omega(0))\cong V^\omega(a),
\qquad
\mathsf{T}^{\omega}_{a+b}\cong
\mathsf{T}^{\omega}_a\circ \mathsf{T}^{\omega}_b,
\qquad
\mathsf{T}^{\omega}_0\cong \id .
\]
In particular, the hypotheses of
Proposition~\ref{prop:yangian-dk5-spectral-vector-seed} are automatic
on any realized spectral vector-line locus (the completed vector seed
and its spectral-shift action are canonically transported from the
standard quantum-loop evaluation line).
\end{proposition}

\begin{proof}
Conjugation by the vector-line equivalence defines
\(\mathsf{T}^{\omega}_a\) on \(\mathcal{L}^{\mathrm{vec}}_{q}\),
and the group law and unit transport from
Proposition~\ref{prop:quantum-fd-vector-seed-shifts} by conjugation.
\end{proof}

\begin{proposition}[On the realized spectral vector-line locus, loop
rotation descends to the full spectral compact core;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-core-shifts}
Work in the setting of
Propositions~\ref{prop:yangian-dk5-spectral-seed-shift-construction}
and~\ref{prop:yangian-dk5-spectral-realization-formal}.  Assume that
the exact braided monoidal functor \(J_q^\omega\) restricts to an
equivalence
\[
\mathcal{L}^{\mathrm{vec,fd}}_{q}\xrightarrow{\sim}
\mathcal{L}^{\mathrm{vec}}_{q}.
\]
Let \(\mathsf{T}^{\omega}_a\) be the induced exact braided-monoidal
autoequivalences of the completed vector line from
Proposition~\ref{prop:yangian-dk5-spectral-seed-shift-construction}.
Then each \(\mathsf{T}^{\omega}_a\) extends uniquely to an exact
braided-monoidal autoequivalence, still denoted
\[
\mathsf{T}^{\omega}_a\colon
\mathcal{C}_q^\omega\xrightarrow{\sim}\mathcal{C}_q^\omega,
\]
and these extensions preserve the completed vector packet, completed
fundamental packet, and completed tensor-generator packet.  Moreover,
\[
\mathsf{T}^{\omega}_{a+b}\cong
\mathsf{T}^{\omega}_a\circ \mathsf{T}^{\omega}_b,
\qquad
\mathsf{T}^{\omega}_0\cong \id
\]
on the full spectral compact core.
\end{proposition}

\begin{proof}
Each \(\mathsf{T}^{\omega}_a\) is exact and braided monoidal on the
completed vector line
(Proposition~\ref{prop:yangian-dk5-spectral-seed-shift-construction}),
hence preserves the ordered vector packet, the completed fundamental
packet (by
Proposition~\ref{prop:yangian-dk5-spectral-vector-packet}), and the
tensor-generator packet.  Since
\(\mathcal{C}_q^\omega=
\operatorname{thick}^{\mathrm{idemp}}(\mathcal{G}^{\mathrm{fund}}_{q})\),
uniqueness of thick-closure extension gives the autoequivalence of
\(\mathcal{C}_q^\omega\) and transports the group law.
\end{proof}

\begin{proposition}[Factorization-locus specializations:
\texorpdfstring{$\rho_a$}{rho\_a} pullback, core from vector line,
seed-line forcing; \ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-factorization-shifts}%
\label{prop:yangian-dk5-spectral-factorization-core-from-vector-line}%
\label{prop:yangian-dk5-spectral-factorization-seed-line}%
Work in the setting of
Definitions~\ref{def:ordered-e1-factorization}
and~\ref{def:spectral-quantum-group}.  Let
\(J_q^{\mathrm{mult}}\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\longrightarrow
\Factord(\bC^\times;\QGspec(R_{\cA}))\)
be an exact braided-monoidal functor, and write
\(\rho_a\colon \bC^\times\xrightarrow{\sim}\bC^\times\),
\(z\mapsto e^a z\), for the multiplicative dilations.
\begin{enumerate}[label=\textup{(\alph*)}]
\item\emph{Intrinsic loop rotation.}
  Assume the spectral compact core \(\mathcal{C}_q^\omega\) is
  realized as a full stable idempotent-complete braided-monoidal
  subcategory of
  \(\Factord(\bC^\times;\QGspec(R_{\cA}))\) closed under
  \(\rho_a^*\).  Then
  \(\mathsf T_a^\omega:=\rho_a^*\colon
  \mathcal C_q^\omega\xrightarrow{\sim}\mathcal C_q^\omega\)
  is an exact braided-monoidal autoequivalence for every
  \(a\in\mathbb C\), with
  \(\mathsf T_{a+b}^\omega\cong
  \mathsf T_a^\omega\circ \mathsf T_b^\omega\) and
  \(\mathsf T_0^\omega\cong \id\).

\item\emph{Core from vector line.}
  Assume \(J_q^{\mathrm{mult}}\) restricts to an equivalence
  \(\mathcal L_q^{\mathrm{vec,fd}}
  \xrightarrow{\sim}
  \mathcal L_q^{\mathrm{vec,mult}}\)
  and each \(\rho_a^*\) preserves
  \(\mathcal L_q^{\mathrm{vec,mult}}\).  Let
  \(\mathcal C_{q,\mathrm{mult}}^\omega\) be the smallest full stable
  idempotent-complete braided-monoidal subcategory containing
  \(\mathcal L_q^{\mathrm{vec,mult}}\).  Then every \(\rho_a^*\)
  restricts to
  \(\mathcal C_{q,\mathrm{mult}}^\omega\xrightarrow{\sim}
  \mathcal C_{q,\mathrm{mult}}^\omega\),
  \(J_q^{\mathrm{mult}}\) is an exact braided-monoidal equivalence
  \(\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
  \xrightarrow{\sim}
  \mathcal C_{q,\mathrm{mult}}^\omega\),
  and \(\mathcal C_{q,\mathrm{mult}}^\omega\) is a multiplicative
  spectral realization of the spectral compact core.

\item\emph{Seed-line forcing.}
  Fix $V(0)\in \mathcal L_q^{\mathrm{vec,fd}}$ and one ambient
  object
  $V^{\mathrm{mult}}(0)\in
  \Factord(\bC^\times;\allowbreak\QGspec(R_{\cA}))$;
  set
  $V^{\mathrm{mult}}(a):=\rho_a^*V^{\mathrm{mult}}(0)$.
  If $J_q^{\mathrm{mult}}$ restricts to an equivalence on the
  one-object subcategory generated by~$V(0)$ and intertwines
  $\mathsf T_a^{\mathrm{fd}}$ with~$\rho_a^*$ on the source
  vector line, then
  $\mathcal L_q^{\mathrm{vec,fd}}
  \xrightarrow{\sim}
  \mathcal L_q^{\mathrm{vec,mult}}$.
\end{enumerate}
\end{proposition}

\begin{proof}
\textup{(a)}
Each \(\rho_a\) is an automorphism of \(\bC^\times\), so \(\rho_a^*\)
is an exact braided-monoidal autoequivalence of the ambient category.
The closure hypothesis restricts it to \(\mathcal C_q^\omega\), and
\(\rho_{a+b}=\rho_a\circ\rho_b\) gives the group law.

\textup{(b)}
\(\rho_a^*\) preserves the generating line by hypothesis, hence the
thick closure.  The source is the thick closure of its vector line
(Lemmas~\ref{lem:quantum-fd-vector-fundamental-generation}
and~\ref{lem:quantum-fd-fundamental-generation}); since
\(J_q^{\mathrm{mult}}\) is exact braided monoidal and an equivalence
on that line, the thick-closure argument of
Proposition~\ref{prop:yangian-dk5-spectral-realization-formal}
upgrades it.

\textup{(c)}
The intertwining forces
\(J_q^{\mathrm{mult}}(V(a))\cong V^{\mathrm{mult}}(a)\), giving
essential surjectivity.  Shifts reduce every Hom pair to
\((V(0),V(b-a))\), and the seed equivalence gives full faithfulness.
\end{proof}

\begin{corollary}[One-seed closure: four variants;
\ClaimStatusProvedHere]
\label{cor:yangian-dk5-spectral-seed-realization}%
\label{cor:yangian-dk5-spectral-one-seed}%
\label{cor:yangian-dk5-spectral-factorization-vector-line}%
\label{cor:yangian-dk5-spectral-factorization-ambient-vector-line}%
Each of the following hypotheses forces the full spectral DK-5 packet:
completed vector line, ordered vector packet, completed fundamental
packet, ordered tensor-generator packet, spectral compact core, and
ambient spectral category are all formal.
\begin{enumerate}[label=\textup{(\alph*)}]
\item\emph{Seed-and-shift datum.}
  Work in the setting of
  Propositions~\ref{prop:quantum-fd-vector-seed-shifts}
  and~\ref{prop:yangian-dk5-spectral-realization-formal}.  Let
  \(J_q^\omega\) be an exact braided monoidal functor to
  \(\mathcal{C}_q^\omega\).  Assume there is a completed vector seed
  \(V^\omega(0)\in \mathcal{C}_q^\omega\), an exact braided-monoidal
  shift family \(\mathsf{T}_a^\omega\) with
  \(\mathsf{T}_{a+b}^\omega\cong
  \mathsf{T}_a^\omega\circ \mathsf{T}_b^\omega\) and
  \(\mathsf{T}_0^\omega\cong \id\), and that setting
  \(V^\omega(a):=\mathsf{T}_a^\omega(V^\omega(0))\), the functor
  \(J_q^\omega\) identifies \(V(0)\) with \(V^\omega(0)\) and
  intertwines source and target shifts.  Then \(J_q^\omega\) restricts
  to an equivalence on the vector line and extends to the full compact
  core and its ind-completion.

\item\emph{One multiplicative seed.}
  Work in the setting of~\textup{(a)} and
  Proposition~\ref{prop:yangian-dk5-spectral-factorization-shifts}.
  If there is a completed vector seed
  \(V^\omega(0)\in \mathcal C_q^\omega\) with
  \(J_q^\omega(V(0))\cong V^\omega(0)\), and \(J_q^\omega\)
  intertwines source shifts with the target pullback family
  \(\mathsf T_a^\omega=\rho_a^*\), then the hypotheses
  of~\textup{(a)} are automatic.

\item\emph{Vector-line realization.}
  Work in the setting of
  Propositions~\ref{prop:yangian-dk5-spectral-vector-line}
  and~\ref{prop:yangian-dk5-spectral-factorization-shifts}.
  If \(J_q^\omega\) restricts to an equivalence
  \(\mathcal L_q^{\mathrm{vec,fd}}
  \xrightarrow{\sim}
  \mathcal L_q^{\mathrm{vec}}\),
  then the hypotheses of~\textup{(a)} are automatic.

\item\emph{Ambient vector-line realization.}
  Assume the hypotheses of
  Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line},
  and let \(\mathcal C_{q,\mathrm{mult}}^\omega\) be the resulting
  multiplicative spectral compact core.  Then \(J_q^{\mathrm{mult}}\)
  restricts to an equivalence on the source vector line, and the
  ordered vector packet, completed fundamental packet, ordered
  tensor-generator packet, compact core, and ambient completed spectral
  category
  \(\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}
  \simeq
  \operatorname{Ind}(\mathcal C_{q,\mathrm{mult}}^\omega)\)
  are all formal from that ambient vector-line realization.
\end{enumerate}
\end{corollary}

\begin{proof}
\textup{(a)}
The shifts preserve \(\mathcal{L}^{\mathrm{vec}}_{q}\), so
Proposition~\ref{prop:yangian-dk5-spectral-vector-seed} forces the
vector-line equivalence.
Propositions~\ref{prop:yangian-dk5-spectral-vector-line},
\ref{prop:yangian-dk5-spectral-vector-packet},
\ref{prop:yangian-dk5-spectral-fundamental-packet}, and
\ref{prop:yangian-dk5-spectral-realization-formal}
promote it through the ordered vector packet,
fundamental packet, generator packet, and full compact core.
Corollary~\ref{cor:yangian-dk5-spectral-packet-ind} gives the
ind-completion.

\textup{(b)}
Proposition~\ref{prop:yangian-dk5-spectral-factorization-shifts}
constructs \(\mathsf T_a^\omega=\rho_a^*\) intrinsically; setting
\(V^\omega(a):=\mathsf T_a^\omega(V^\omega(0))\) recovers the
hypotheses of~\textup{(a)}.

\textup{(c)}
Propositions~\ref{prop:quantum-fd-vector-seed-shifts}
and~\ref{prop:yangian-dk5-spectral-seed-shift-construction} construct
and transport the seed-and-shift datum;
Proposition~\ref{prop:yangian-dk5-spectral-core-shifts} extends it to
the compact core.  On the multiplicative locus, the target shifts are
intrinsic by
Proposition~\ref{prop:yangian-dk5-spectral-factorization-shifts}.

\textup{(d)}
Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line}
constructs the compact core;~\textup{(c)} gives the sub-packet
formality; Corollary~\ref{cor:yangian-dk5-spectral-packet-ind} gives
the ambient ind-completion.
\end{proof}

\begin{corollary}[Schur-simple ambient seed criterion for the
multiplicative spectral vector line; \ClaimStatusProvedHere]
\label{cor:yangian-dk5-spectral-factorization-schur-seed-line}
Work in the setting of
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}.
Assume that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item there is an isomorphism
  \[
  J_q^{\mathrm{mult}}(V(0))\cong V^{\mathrm{mult}}(0);
  \]
\item the ambient seed is Schur-simple:
  \[
  \End(V^{\mathrm{mult}}(0))\cong \mathbb C;
  \]
\item on the source vector line,
  \(J_q^{\mathrm{mult}}\) intertwines the standard source loop-rotation
  autoequivalences \(\mathsf T_a^{\mathrm{fd}}\) with the ambient
  dilation pullbacks \(\rho_a^*\).
\end{enumerate}
Then the hypotheses of
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}
are automatic.  Consequently the restriction of \(J_q^{\mathrm{mult}}\)
to the source vector line is an exact braided-monoidal equivalence
\[
\mathcal L_q^{\mathrm{vec,fd}}
\xrightarrow{\sim}
\mathcal L_q^{\mathrm{vec,mult}}.
\]

\end{corollary}

\begin{proof}
Schur simplicity on both sides
(Lemma~\ref{lem:quantum-fd-vector-seed-schur} and
assumption~\textup{(ii)}) makes the one-object subcategories
equivalent after choosing~\textup{(i)}.  Apply
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}.
\end{proof}

\begin{corollary}[One ambient multiplicative vector seed closes the
spectral DK-5 side; \ClaimStatusProvedHere]
\label{cor:yangian-dk5-spectral-factorization-ambient-one-seed}
Assume the hypotheses of
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}.
Let
\[
\mathcal C_{q,\mathrm{mult}}^\omega
\subset
\Factord(\bC^\times;\QGspec(R_{\cA}))
\]
be the smallest full stable idempotent-complete braided-monoidal
subcategory containing the ambient dilation orbit
\(\mathcal L_q^{\mathrm{vec,mult}}\) of \(V^{\mathrm{mult}}(0)\).
Then:
\begin{enumerate}[label=\textup{(\alph*)}]
\item \(\mathcal C_{q,\mathrm{mult}}^\omega\) is exactly the
  multiplicative spectral compact core forced by that single ambient
  vector seed;
\item the completed vector line, ordered vector packet, completed
  fundamental packet, ordered tensor-generator packet, compact core,
  and ambient completed spectral category are all formal from that
  seed.
\end{enumerate}

\end{corollary}

\begin{proof}
Apply
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}
to verify the hypotheses of
Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line},
then
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-vector-line}.
\end{proof}

\begin{corollary}[One Schur-simple ambient multiplicative vector seed
closes the spectral DK-5 side; \ClaimStatusProvedHere]
\label{cor:yangian-dk5-spectral-factorization-ambient-schur-seed}
Work in the setting of
Corollary~\ref{cor:yangian-dk5-spectral-factorization-schur-seed-line}.
Let
\[
\mathcal C_{q,\mathrm{mult}}^\omega
\subset
\Factord(\bC^\times;\QGspec(R_{\cA}))
\]
be the smallest full stable idempotent-complete braided-monoidal
subcategory containing the ambient dilation orbit
\(\mathcal L_q^{\mathrm{vec,mult}}\) of \(V^{\mathrm{mult}}(0)\).
Then the completed vector line, ordered vector packet, completed
fundamental packet, ordered tensor-generator packet, compact core, and
ambient completed spectral category are all formal from that single
Schur-simple ambient vector seed.

\end{corollary}

\begin{proof}
Corollary~\ref{cor:yangian-dk5-spectral-factorization-schur-seed-line}
supplies the hypotheses of
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-one-seed}.
\end{proof}

\begin{theorem}[Spectral DK-5 seed-pair reduction hierarchy;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-spectral-factorization-seed-mono}%
\label{cor:yangian-dk5-spectral-factorization-seed-mono}%
\label{prop:yangian-dk5-spectral-factorization-seed-trig}%
\label{cor:yangian-dk5-spectral-factorization-seed-trig}%
\label{prop:yangian-dk5-spectral-factorization-seed-channels}%
\label{cor:yangian-dk5-spectral-factorization-seed-single-line}%
\label{prop:yangian-dk5-spectral-factorization-seed-exchange}%
\label{cor:yangian-dk5-spectral-factorization-seed-exchange-mult}%
\label{prop:yangian-dk5-spectral-factorization-seed-alt-mult}%
Work in the setting of
Definitions~\ref{def:ordered-e1-factorization}
and~\ref{def:spectral-quantum-group}.  Fix one ambient object
\(V^{\mathrm{mult}}(0)\in \Factord(\bC^\times;\QGspec(R_{\cA}))\)
and define its dilation orbit by
\(V^{\mathrm{mult}}(a):=\rho_a^*V^{\mathrm{mult}}(0)\).
For \(a,b\in\mathbb C\), write
\(\mathsf B_{a,b}^{\mathrm{mult}}\) for the ambient two-point braid
monodromy operator and \(\mathsf B_{a,b}^{\mathrm{fd}}\) for the
source two-point trigonometric braid operator on the standard
quantum-loop vector line.  Then the following successive reductions
hold.
\begin{enumerate}[label=\textup{(\alph*)}]
\item\emph{Monodromy from seed pair.}
  After the canonical identification
  \(V^{\mathrm{mult}}(a)\boxtimes V^{\mathrm{mult}}(b)
  \cong \rho_a^*(V^{\mathrm{mult}}(0)\boxtimes V^{\mathrm{mult}}(b-a))\),
  one has
  \(\mathsf B_{a,b}^{\mathrm{mult}}
  \cong \rho_a^*(\mathsf B_{0,b-a}^{\mathrm{mult}})\).
  On every ordered tensor product, the full braid-group action is
  generated by the one-parameter family
  \(\{\mathsf B_{0,c}^{\mathrm{mult}}\}_{c\in\mathbb C}\) via
  dilation pullbacks.  After the Schur-simple ambient seed, the only
  remaining local geometric datum is that seed-pair monodromy family.

\item\emph{Trigonometric identity.}
  The braid-group action on the ambient vector packet agrees with the
  standard source trigonometric action if and only if
  \(\mathsf B_{0,c}^{\mathrm{mult}} \cong
  \mathsf B_{0,c}^{\mathrm{fd}}\) for every \(c\in\mathbb C\).

\item\emph{Channel decomposition.}
  Assume moreover that for every \(c\), both
  \(\mathsf B_{0,c}^{\mathrm{fd}}\) and
  \(\mathsf B_{0,c}^{\mathrm{mult}}\) intertwine the diagonal
  \(\mathfrak{sl}_M\)-action on \(V\otimes V\).  Then the
  trigonometric seed-pair identity holds if and only if the two
  operators act by the same scalar on \(\operatorname{Sym}^2(V)\) and
  on \(\Lambda^2(V)\); equivalently, it is enough to check on
  \(e_1\otimes e_1\) and \(e_1\otimes e_2-e_2\otimes e_1\).

\item\emph{Mixed-tensor reduction.}
  Assume \(M\ge 2\) and that for every \(c\) the source and ambient
  operators agree on the highest-weight line
  (\(\mathsf B_{0,c}^{\mathrm{mult}}(e_1\otimes e_1)
  = \mathsf B_{0,c}^{\mathrm{fd}}(e_1\otimes e_1)\)).
  Then the trigonometric identity holds if and only if the single
  mixed-tensor identity
  \(\mathsf B_{0,c}^{\mathrm{mult}}(e_1\otimes e_2)
  = \mathsf B_{0,c}^{\mathrm{fd}}(e_1\otimes e_2)\) holds.

\item\emph{Exchange coefficient.}
  Under the hypotheses of~\textup{(d)}, write
  \(\mathsf B_{0,c}^{\bullet}(e_1\otimes e_2)
  = \alpha^{\bullet}(c)\,e_1\otimes e_2
  + \beta^{\bullet}(c)\,e_2\otimes e_1\)
  for \(\bullet\in\{\mathrm{fd},\mathrm{mult}\}\).
  Then the trigonometric identity is equivalent to the single scalar
  identity \(\beta^{\mathrm{mult}}(c)=\beta^{\mathrm{fd}}(c)\).
  Both families are \(2\pi i\)-periodic, hence descend to functions
  \(\beta_\times^{\mathrm{fd}},\beta_\times^{\mathrm{mult}}\) of the
  multiplicative ratio \(e^c\), and the identity becomes
  \(\beta_\times^{\mathrm{mult}}=\beta_\times^{\mathrm{fd}}\).

\item\emph{Antisymmetric-channel character.}
  Under the hypotheses of~\textup{(e)}, there exist unique scalar
  functions
  \(\lambda_{\mathrm{alt},\times}^{\mathrm{fd}},
  \lambda_{\mathrm{alt},\times}^{\mathrm{mult}}\) of the
  multiplicative spectral ratio such that
  \(\mathsf B_{0,c}^{\bullet}(e_1\otimes e_2-e_2\otimes e_1)
  = \lambda_{\mathrm{alt},\times}^{\bullet}(e^c)
  (e_1\otimes e_2-e_2\otimes e_1)\).
  The trigonometric seed-pair identity is equivalent to
  \(\lambda_{\mathrm{alt},\times}^{\mathrm{mult}}
  = \lambda_{\mathrm{alt},\times}^{\mathrm{fd}}\).
\end{enumerate}
\end{theorem}

\begin{proof}
\textup{(a)}
Functoriality of \(\rho_a^*\) transports
\(\mathsf B_{0,b-a}^{\mathrm{mult}}\) to
\(\mathsf B_{a,b}^{\mathrm{mult}}\).
\(B_n\) is generated by adjacent transpositions, and each adjacent
operator is obtained from the seed-pair family by dilation pullback.
The Schur-simple reduction follows from
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-schur-seed}.

\textup{(b)}
The source braid-group action is generated by
\(\{\mathsf B_{0,c}^{\mathrm{fd}}\}\) via the same dilation argument
(using \(\mathsf T_a^{\mathrm{fd}}\) in place of \(\rho_a^*\)).
Since both sides are generated by their respective seed-pair families,
the full actions agree if and only if the seed-pair families agree.

\textup{(c)}
Diagonal \(\mathfrak{sl}_M\)-equivariance forces both operators to
preserve
\(V\otimes V\cong \operatorname{Sym}^2(V)\oplus \Lambda^2(V)\).
Schur's lemma reduces the comparison to two channel scalars, detected
by the highest-weight generators.

\textup{(d)}
The highest-weight normalization forces
\(\lambda_{\mathrm{sym}}^{\mathrm{mult}}(c)=
\lambda_{\mathrm{sym}}^{\mathrm{fd}}(c)\).
Writing \(e_1\otimes e_2=\frac12(s+a)\) with
\(s\in\operatorname{Sym}^2(V)\), \(a\in\Lambda^2(V)\), the
mixed-tensor identity and linear independence of \(e_1\otimes e_2\)
and \(e_2\otimes e_1\) force the antisymmetric channel scalar to
agree as well, giving~\textup{(c)}.

\textup{(e)}
Under the common symmetric channel scalar, the exchange coefficient
satisfies
\(\beta(c)=(\lambda_{\mathrm{sym}}(c)-\lambda_{\mathrm{alt}}(c))/2\),
so \(\beta^{\mathrm{mult}}=\beta^{\mathrm{fd}}\) is equivalent to
equality of channel scalars and hence of full mixed-tensor outputs.
Both families are \(2\pi i\)-periodic (\(V(c+2\pi i)\cong V(c)\) on
the source, \(\rho_{c+2\pi i}=\rho_c\) on the ambient side), hence
descend to the multiplicative ratio.

\textup{(f)}
The antisymmetric channel scalars are likewise \(2\pi i\)-periodic,
hence descend to multiplicative-ratio functions.  Under highest-weight
normalization, equality of exchange coefficients is equivalent to
equality of these antisymmetric-channel characters.
\end{proof}

\begin{corollary}[On the realized spectral packet locus, the ambient
spectral category is the ind-completion of the spectral compact core;
\ClaimStatusProvedHere]
\label{cor:yangian-dk5-spectral-packet-ind}
Assume the hypotheses of
Proposition~\ref{prop:yangian-dk5-spectral-realization-formal}.  On
this realized packet locus, define the ambient completed spectral
category by
\[
\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}
:=
\operatorname{Ind}(\mathcal{C}_q^\omega).
\]
Then
\(\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}\)
is presentable, stable, and compactly generated, and its compact
objects are exactly \(\mathcal{C}_q^\omega\).  Equivalently, there is a
canonical exact colimit-preserving equivalence
\[
\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}
\xrightarrow{\sim}
\operatorname{Ind}(\mathcal{C}_q^\omega).
\]
In particular, the ambient completed spectral category is compactly
generated by the completed fundamental spectral packet
\(\mathcal{G}^{\mathrm{fund}}_{q}\).
\end{corollary}

\begin{proof}
Apply Theorem~\ref{thm:ind-completed-extension} to the small stable
idempotent-complete category \(\mathcal{C}_q^\omega\).
\end{proof}

\begin{proposition}[Canonical completed dg fundamental packet from the
theorematic finite RTT quotients; \ClaimStatusProvedHere]
\label{prop:yangian-dg-fundamental-packet-realization}
Assume the data and hypotheses \textup{(i)}--\textup{(vii)} of
Proposition~\ref{prop:yangian-typea-realization-criterion}.  Let
\[
\mathcal{G}^{\mathrm{fund,fd}}_{Y}
\subset
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\]
be the full subcategory generated by finite ordered tensor products of
fundamental evaluation objects.  For
\(M\in\mathcal{G}^{\mathrm{fund,fd}}_{Y}\), let \(M_{\le N}\) be its
standard finite-stage evaluation image over \(Y_{\le N}\) under the
compatible quotient comparison of
assumption~\textup{(vi)}.  Then the tower \(\{M_{\le N}\}_N\) defines a
continuous completed dg module
\[
J_{Y,\mathrm{pkt}}^\omega(M)
:=
\varprojlim_N M_{\le N}
\]
over \(\Ydg_{\cA}\), and these assignments assemble into a canonical
exact braided monoidal functor
\[
J_{Y,\mathrm{pkt}}^\omega\colon
\mathcal{G}^{\mathrm{fund,fd}}_{Y}
\longrightarrow
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA}).
\]
Let \(\mathcal{G}^{\mathrm{fund}}_{Y}\) denote its essential image.
Then \(J_{Y,\mathrm{pkt}}^\omega\) is an exact braided monoidal
equivalence
\[
\mathcal{G}^{\mathrm{fund,fd}}_{Y}
\xrightarrow{\sim}
\mathcal{G}^{\mathrm{fund}}_{Y}.
\]

\end{proposition}

\begin{proof}
Assumption~\textup{(vi)} identifies each finite quotient with
\(Y_{\le N}\) compatibly with evaluation modules.  The inverse limit
\(\varprojlim_N M_{\le N}\) is then a continuous module over
\(\Ydg_{\cA}\) by assumption~\textup{(v)}.  Exactness and braided
monoidality are checked stagewise using
assumptions~\textup{(i)}--\textup{(iv)} and~\textup{(vi)}.
\end{proof}

\begin{proposition}[Canonical exact braided-monoidal extension of the
dg packet; \ClaimStatusProvedHere]
\label{prop:yangian-dk5-dg-extension-existence}
Assume the hypotheses of
Proposition~\ref{prop:yangian-dg-fundamental-packet-realization}.  Let
\[
\mathcal{C}_Y^\omega
:=
\operatorname{thick}^{\mathrm{idemp}}
\bigl(\mathcal{G}^{\mathrm{fund}}_{Y}\bigr)
\subset
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA}).
\]
Then the packet functor \(J_{Y,\mathrm{pkt}}^\omega\) extends to an
exact braided monoidal functor
\[
J_Y^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
\longrightarrow
\mathcal{C}_Y^\omega
\]
whose restriction to \(\mathcal{G}^{\mathrm{fund,fd}}_{Y}\) is
\(J_{Y,\mathrm{pkt}}^\omega\).  This extension is unique up to unique
natural isomorphism.

\end{proposition}

\begin{proof}
The stable idempotent-complete braided monoidal target
\(\mathcal{C}_Y^\omega\) allows unique thick-closure extension of
\(J_{Y,\mathrm{pkt}}^\omega\) from
\(\mathcal{G}^{\mathrm{fund,fd}}_{Y}\) to the full source
(Lemma~\ref{lem:yangian-fd-fundamental-generation}).  Uniqueness
follows as in
Proposition~\ref{prop:yangian-dk3-generated-core}.
\end{proof}

\begin{proposition}[dg compact-core realization is formal from
extension of the completed fundamental packet;
\ClaimStatusProvedHere]
\label{prop:yangian-dk5-dg-realization-formal}
Assume the hypotheses of
Proposition~\ref{prop:yangian-dk5-dg-extension-existence}.  Let
\[
\mathcal{C}_Y^\omega
:=
\operatorname{thick}^{\mathrm{idemp}}
\bigl(\mathcal{G}^{\mathrm{fund}}_{Y}\bigr)
\subset
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA}).
\]
Then \(J_Y^\omega\) is an exact braided monoidal equivalence.

\end{proposition}

\begin{proof}
Since \(J_Y^\omega\) is exact braided monoidal and an equivalence on
\(\mathcal{G}^{\mathrm{fund,fd}}_{Y}\), the thick-closure argument of
Proposition~\ref{prop:yangian-dk5-spectral-realization-formal} upgrades
it to an equivalence on the full closures
(Lemma~\ref{lem:yangian-fd-fundamental-generation}).
\end{proof}

\begin{corollary}[Compact generation of the completed dg module
category identifies the ambient dg side with the ind-completion of the
dg compact core;
\ClaimStatusProvedHere]
\label{cor:yangian-dk5-dg-packet-ind}
Assume the hypotheses of
Proposition~\ref{prop:yangian-dk5-dg-realization-formal}.  On this
realized packet locus, define the ambient completed dg module category
by
\[
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
:=
\operatorname{Ind}(\mathcal{C}_Y^\omega).
\]
Then \(\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})\) is presentable,
stable, and compactly generated, and its compact objects are exactly
\(\mathcal{C}_Y^\omega\).  Equivalently, there is a canonical exact
colimit-preserving equivalence
\[
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\xrightarrow{\sim}
\operatorname{Ind}(\mathcal{C}_Y^\omega).
\]
In particular, \(\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})\) is
compactly generated by the completed fundamental dg-shifted packet
\(\mathcal{G}^{\mathrm{fund}}_{Y}\).

\end{corollary}

\begin{proof}
Apply Theorem~\ref{thm:ind-completed-extension} to the small stable
idempotent-complete category \(\mathcal{C}_Y^\omega\).
\end{proof}

\begin{corollary}[Given dg compact-core realization, the remaining
DK-5 input is spectral vector seed-and-shift realization;
\ClaimStatusProvedHere]
\label{cor:yangian-dk5-dg-half-only}
Assume the hypotheses of
Corollary~\ref{cor:yangian-typea-dg-local-closure}.  Assume moreover
that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the completed dg-shifted and spectral categories are presentable,
  stable, and compactly generated, with compact objects exactly
  \(\mathcal{C}_Y^\omega\) and \(\mathcal{C}_q^\omega\);
\item the spectral compact core admits an exact braided monoidal
  functor \(J_q^\omega\) whose restriction to the vector evaluation
  line is an equivalence onto the completed vector spectral line, as in
  Proposition~\ref{prop:yangian-dk5-spectral-vector-line}; and
\item there exists an exact braided monoidal equivalence
  \[
  J_Y^\omega\colon
  \operatorname{Fact}_{\Eone}^{\mathrm{fd}}(Y_\hbar(\mathfrak{sl}_M))
  \xrightarrow{\sim}
  \mathcal{C}_Y^\omega
  \]
  identifying the fundamental evaluation objects with the completed
  fundamental dg-shifted packet.
\end{enumerate}
Then the standard type-$A$ Yangian DK-5 packet closes.

\end{corollary}

\begin{proof}
Propositions~\ref{prop:quantum-fd-vector-seed-shifts},
\ref{prop:yangian-dk5-spectral-seed-shift-construction},
and~\ref{prop:yangian-dk5-spectral-core-shifts} transport the standard
seed-and-shift datum to the spectral compact core.
Corollary~\ref{cor:yangian-dk5-spectral-seed-realization} closes the
spectral packet.  Together with the dg hypotheses,
Corollary~\ref{cor:yangian-dk5-core-realization} closes DK-5.
\end{proof}

\begin{corollary}[DK-5 closes once the compact cores realize the
proved finite-dimensional factorization DK core; \ClaimStatusProvedHere]
\label{cor:yangian-dk5-core-realization}
Assume the hypotheses of
Corollary~\ref{cor:yangian-typea-dg-local-closure}.  Assume moreover
that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the completed dg-shifted and spectral categories are presentable,
  stable, and compactly generated, with compact objects exactly
  $\mathcal{C}_Y^\omega$ and $\mathcal{C}_q^\omega$;
\item the compact cores are exact braided monoidal realizations of the
  proved finite-dimensional factorization DK pair of
  Theorem~\ref{thm:dk-fd-typeA} in the sense of
  Proposition~\ref{prop:yangian-dk5-core-realization}.
\end{enumerate}
Then the standard type-$A$ Yangian DK-5 packet closes.

\end{corollary}

\begin{proof}
Apply Proposition~\ref{prop:yangian-dk5-core-realization} for the
compact-core equivalence, then
Proposition~\ref{prop:yangian-dk5-ind-extension} for the ambient
extension.
\end{proof}

\begin{corollary}[Type-\texorpdfstring{$A$}{A} MC4 reduction chain:
  five closure criteria; \ClaimStatusProvedHere]
\label{cor:yangian-typea-mc4-closure-criterion}%
\label{cor:yangian-typea-degree2-plus-generators}%
\label{cor:yangian-typea-casimir-plus-generators}%
\label{cor:yangian-typea-factorization-local-closure}%
\label{cor:yangian-typea-shared-seed-plus-generators}%
Assume the hypotheses of
Propositions~\ref{prop:yangian-dk4-typea-frontier}
and~\ref{prop:yangian-dk5-compact-generators}.
The standard type-$A$ Yangian MC4 packet admits the following
successive reductions.
\begin{enumerate}[label=\textup{(\roman*)}]
\item\emph{Minimal closure.}
  MC4 closes once the dg-shifted or factorization one-factor kernel is
  identified with the standard normalized RTT residue on the
  fundamental evaluation line---under the symmetry and normalization
  hypotheses of
  Proposition~\ref{prop:yangian-dk4-typea-frontier} this is equivalent
  to
  \(
  \Xi_a(e_1\otimes e_2)=-\hbar(e_2\otimes e_1)
  \)---and the compact-generator comparison
  $\mathcal{G}^{\mathrm{fund}}_Y \to \mathcal{G}^{\mathrm{fund}}_q$
  is an equivalence.

\item\emph{One-loop exactness.}
  Assume moreover the one-loop exactness and seed-normalization
  hypotheses of
  Proposition~\ref{prop:dg-shifted-rtt-degree2-mixed-tensor-criterion}
  and
  Corollary~\ref{cor:dg-shifted-rtt-seed-normalized-coefficient} on
  the standard type-$A$ fundamental line.  Then the remaining MC4
  input is the single degree-$2$ coefficient identity
  \[
  r_a^{\mathrm{fund}}(z)(e_1\otimes e_2)
  =
  -\hbar(e_2\otimes e_1),
  \]
  where $r_a^{\mathrm{fund}}(z)$ is induced by
  $r(z)=\tau|_{\deg 2}$ on the ordered fundamental line, together
  with the compact-generator comparison.

\item\emph{Casimir insertion.}
  If, moreover, the ordered fundamental-line degree-$2$ coefficient is
  the standard trace-zero Casimir insertion
  \[
  r_a^{\mathrm{fund}}(z)\big|_{z_1=z_2}
  =
  -\hbar\,\Omega_{\mathfrak{sl}_M}^{\mathrm{fund}}
  =
  -\hbar\Bigl(P-\frac{1}{M}\id\Bigr),
  \]
  then the local coefficient identity~\textup{(ii)} is automatic, and
  the remaining MC4 input is compact generation plus transport on the
  completed fundamental evaluation packet.

\item\emph{Factorization closure.}
  On the ordered factorization target,
  Corollary~\ref{cor:factorization-fundamental-casimir-identity}
  supplies the Casimir hypothesis of~\textup{(iii)} automatically.
  Hence the remaining MC4 input on the factorization side is compact
  generation plus fundamental-packet transport.

\item\emph{Shared seed closure.}
  Assume the hypotheses of~\textup{(iv)} on the ordered factorization
  target and of
  Corollary~\ref{cor:yangian-typea-dg-local-closure} on an ordered
  dg-shifted target presented by the same ordered bar seed.  Then the
  local MC4 packet is automatic on both sides, and the remaining
  standard type-$A$ Yangian MC4 input is exactly the compact-generator
  comparison
  \[
  \mathcal{G}^{\mathrm{fund}}_Y
  \xrightarrow{\sim}
  \mathcal{G}^{\mathrm{fund}}_q.
  \]
\end{enumerate}
\end{corollary}

\begin{proof}
\textup{(i)}
Proposition~\ref{prop:yangian-dk4-typea-frontier} reduces DK-4 to the
mixed-tensor coefficient;
Proposition~\ref{prop:dg-shifted-rtt-degree2-fundamental-casimir}
and Corollary~\ref{cor:factorization-fundamental-casimir-identity}
show the Casimir insertion forces it.
Proposition~\ref{prop:yangian-dk5-compact-generators} reduces DK-5 to
compact generators.

\textup{(ii)}
Corollary~\ref{cor:dg-shifted-rtt-seed-normalized-coefficient}
identifies the residue with the degree-$2$ coefficient.  Under
one-loop exactness
(Proposition~\ref{prop:dg-shifted-rtt-degree2-mixed-tensor-criterion}),
this forces the DK-4 content of
Proposition~\ref{prop:yangian-dk4-typea-frontier}.  The remaining
DK-5 input is
Corollary~\ref{cor:yangian-dk5-fundamental-packet}.

\textup{(iii)}
Proposition~\ref{prop:dg-shifted-rtt-degree2-fundamental-casimir}
forces \(\beta_a=-1\), which gives the coefficient
identity~\textup{(ii)}.

\textup{(iv)}
Corollary~\ref{cor:factorization-fundamental-casimir-identity}
supplies the Casimir hypothesis of~\textup{(iii)}.

\textup{(v)}
Part~\textup{(iv)} closes the factorization side;
Corollary~\ref{cor:yangian-typea-dg-local-closure} transports via
the shared seed.
Proposition~\ref{prop:yangian-dk5-compact-generators} reduces the
remaining DK-5 packet to compact generators.
\end{proof}

\begin{remark}[Exact extra input for DK-5]
\label{rem:yangian-dk5-input}
After Proposition~\ref{prop:yangian-dk4-typea-frontier}, the remaining
DK-5 packet is the compact-core categorical packet:
\textup{(i)}~on the dg side,
Propositions~\ref{prop:yangian-dg-fundamental-packet-realization},
\ref{prop:yangian-dk5-dg-extension-existence},
and~\ref{prop:yangian-dk5-dg-realization-formal} construct and extend
the canonical dg packet, and
Corollary~\ref{cor:yangian-dk5-dg-packet-ind} removes the remaining
dg frontier;
\textup{(ii)}~on the spectral side, realize the standard vector
seed-and-shift datum
(Propositions~\ref{prop:quantum-fd-vector-seed-shifts},
\ref{prop:yangian-dk5-spectral-seed-shift-construction},
\ref{prop:yangian-dk5-spectral-core-shifts})---on the multiplicative
locus this contracts to one Schur-simple ambient vector seed
(Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-schur-seed})
and then to one antisymmetric-channel character
(Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-alt-mult});
\textup{(iii)}~with both compact-core realizations,
Corollary~\ref{cor:yangian-dk5-core-realization} closes DK-5 via
ind-extension (Proposition~\ref{prop:yangian-dk5-ind-extension}).
\end{remark}

\begin{remark}[MC4 boundary for Yangian towers]
\label{rem:yangian-mc4-boundary}
The finite RTT Yangians are theorematic (bar-cobar, $R\mapsto R^{-1}$,
evaluation-locus DK square).  The genuine MC4 input is
Hypothesis~\textup{(ii)} of Conjecture~\ref{conj:full-dk-bridge}: the
RTT-adapted realization of the canonical H-level target
(Proposition~\ref{prop:yangian-canonical-hlevel-target}).
The standard RTT tower supplies the completed M-level package
(Corollary~\ref{cor:yangian-standard-mc4-package}), and
Corollary~\ref{cor:yangian-hlevel-comparison-criterion} makes the
comparison formal once finite quotients recover the proved stages.
For standard type-$A$,
Proposition~\ref{prop:yangian-dk4-typea-frontier} sharpens DK-4 to
one mixed-tensor residue check, and the DK-5 packet reduces to compact
generation plus fundamental-packet transport (see
Remark~\ref{rem:yangian-dk5-input}).  On the spectral side, the
reduction chain contracts the live input to one antisymmetric-channel
character on the multiplicative spectral line
(Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-alt-mult}).
MC5 begins only after this H-level comparison packet is in place.
\end{remark}

\begin{remark}[What the Yangian tower still has to prove]
\label{rem:yangian-mc4-checklist}
By Proposition~\ref{prop:mc4-reduction-principle}, the Yangian-tower
frontier breaks into four checks:
\textup{(1)}~finite RTT truncations in the proved $\Eone$-Koszul regime;
\textup{(2)}~compatible descent of finite-stage bar/cobar
(Proposition~\ref{prop:inverse-limit-differential-continuity});
\textup{(3)}~Mittag--Leffler on
$\{H^m(\bar B(Y_{\le N}))\}_N$
(Corollary~\ref{cor:yangian-weight-cutoff});
\textup{(4)}~inverse-limit identification
(Proposition~\ref{prop:yangian-rtt-completion-identification}).
Items~\textup{(1)}--\textup{(3)} are theorematic for the standard RTT
tower.  For~\textup{(4)},
Corollary~\ref{cor:yangian-hlevel-comparison-criterion} reduces the
H-level comparison to constructing a filtered model whose finite
quotients match the proved stages; in type~$A$,
Proposition~\ref{prop:yangian-dk4-typea-frontier} reduces this to one
residue check, and the dg fundamental packet is already constructed by
Proposition~\ref{prop:yangian-dg-fundamental-packet-realization}.
\end{remark}

\begin{proposition}[Yangian tower criterion from finite RTT stages;
\ClaimStatusProvedHere]
\label{prop:yangian-tower-mc4-criterion}
Let
\[
Y = \varprojlim_N Y_{\le N}
\]
be a separated complete Yangian tower assembled from finite RTT stages.
Assume:
\begin{enumerate}
\item each $Y_{\le N}$ lies in the proved $\Eone$-Koszul regime of this
  chapter;
\item the transition maps $Y_{\le N+1} \to Y_{\le N}$ are compatible
  with the finite-stage bar complexes and bar-cobar
  quasi-isomorphisms;
\item for every cohomological degree~$m$, the inverse system
  $\{H^m(\bar B(Y_{\le N}))\}_N$ is eventually constant; and
\item the transition maps define an inverse system of curved dg
  coalgebras on the finite-stage bar complexes.
\end{enumerate}
Then the completed Yangian bar object
\[
\widehat{\bar B}(Y) := \varprojlim_N \bar B(Y_{\le N})
\]
is a separated complete pro-nilpotent curved dg coalgebra and the
canonical comparison map
\[
\Omega\bigl(\widehat{\bar B}(Y)\bigr) \xrightarrow{\sim} Y
\]
is a quasi-isomorphism.  This gives the M-level completed bar-cobar
package for the Yangian tower under the stated inverse-limit
hypotheses.  The stronger H-level
higher-level factorization-categorical realization remains part of the
MC4 frontier; MC5 is downstream of that realization.  As in the \(\mathcal{W}_\infty\) case, the eventual-constancy
hypothesis may be weakened to eventual surjectivity on finite-dimensional
weight slices by Corollary~\ref{cor:mc4-surjective-criterion}.
\end{proposition}

\begin{proof}
Assumption~\textup{(iii)} is exactly the stabilization hypothesis of
Corollary~\ref{cor:mc4-degreewise-stabilization}, and
Assumptions~\textup{(i)}, \textup{(ii)}, and~\textup{(iv)} identify the
Yangian tower with the general inverse-limit setting of
Proposition~\ref{prop:mc4-reduction-principle}, while
Proposition~\ref{prop:inverse-limit-differential-continuity} supplies
the continuity of the completed bar and cobar differentials.
Applying Corollary~\ref{cor:mc4-degreewise-stabilization} to the tower
$\{\bar B(Y_{\le N})\}_N$ yields the stated completed bar-cobar
quasi-isomorphism.
\end{proof}

\begin{corollary}[Standard RTT cutoff for Yangian towers;
\ClaimStatusProvedHere]
\label{cor:yangian-weight-cutoff}
Let $Y_{\le N}$ be the standard RTT truncation retaining the generators
$T_{ij}^{(r)}$ with $r \le N$, and let
$Y = \varprojlim_N Y_{\le N}$ be the resulting inverse-limit tower.
Then the tower of bar complexes $\{\bar B(Y_{\le N})\}_N$ satisfies the
hypotheses of Proposition~\ref{prop:mc4-weight-cutoff} for the total
RTT-level filtration.  In particular, for every cohomological degree
$m$ and total RTT level $\ell$, the map
\[
H^m(\bar B(Y_{\le N+1}))_\ell \xrightarrow{\sim}
H^m(\bar B(Y_{\le N}))_\ell
\]
is an isomorphism for all $N \ge \ell$.

Therefore the standard RTT tower already supplies the
surjectivity/stabilization part of MC4.  Together with
Proposition~\ref{prop:inverse-limit-differential-continuity} and
Proposition~\ref{prop:yangian-rtt-completion-identification}, this
reduces the standard RTT tower to the standard-RTT completed M-level
package of Corollary~\ref{cor:yangian-standard-mc4-package}.
\end{corollary}

\begin{proof}
The RTT generators are graded by level~$r$, and the RTT relation is
homogeneous in the total level (Theorem~\ref{thm:yangian-koszul-dual},
Step~2a).  A bar chain of total RTT level $\ell$ can therefore involve
only generators $T_{ij}^{(r)}$ with $r \le \ell$.  Once $N \ge \ell$,
all such generators already lie in the truncation $Y_{\le N}$, so the
filtered bar subcomplex of levels $\le \ell$ is identical in every
later stage.  Proposition~\ref{prop:mc4-weight-cutoff} then gives the
stated stabilization on cohomology slices.
\end{proof}

\begin{proposition}[Inverse-limit identification of the standard RTT
completion; \ClaimStatusProvedHere]
\label{prop:yangian-rtt-completion-identification}
Let $\widehat Y_{\mathrm{RTT}}$ be the coefficientwise RTT completion:
its elements are formal matrices
\[
T(u)=1+\hbar\sum_{r \ge 0} T^{(r)}u^{-r-1}
\]
satisfying the RTT relation coefficientwise, with topology of
coefficientwise convergence in the modes $T_{ij}^{(r)}$.  Then the
canonical truncation maps identify this completed RTT algebra with the
standard inverse-limit tower:
\[
\widehat Y_{\mathrm{RTT}} \xrightarrow{\sim} \varprojlim_N Y_{\le N}.
\]
\end{proposition}

\begin{proof}
For each $N$, truncating the formal matrix after level~$N$ produces
\[
T_{\le N}(u)=1+\hbar\sum_{r=0}^N T^{(r)}u^{-r-1},
\]
which satisfies the finite RTT relations defining $Y_{\le N}$ because
every coefficient of the RTT equation only involves finitely many modes.
This gives compatible algebra maps
$q_N\colon \widehat Y_{\mathrm{RTT}} \to Y_{\le N}$ and hence a map
\[
q\colon \widehat Y_{\mathrm{RTT}} \longrightarrow \varprojlim_N Y_{\le N}.
\]

Conversely, let $(x_N)_N$ be a compatible family in the inverse limit.
Represent $x_N$ by a truncated RTT matrix
$T^{(\le N)}(u)=1+\hbar\sum_{r=0}^N T_N^{(r)}u^{-r-1}$.
Compatibility of the truncation maps implies that for each fixed
$r \ge 0$, the coefficient $T_N^{(r)}$ is independent of $N$ once
$N \ge r$; denote the stable value by $T^{(r)}$.  These stable
coefficients assemble into a formal RTT matrix
\[
T(u)=1+\hbar\sum_{r \ge 0} T^{(r)}u^{-r-1}.
\]
To verify the RTT relation coefficientwise, fix a coefficient of
$u^{-a-1}v^{-b-1}$.  That coefficient depends only on modes
$T^{(r)}$ with $r \le \max\{a,b\}+1$, so it is already visible in every
finite truncation $Y_{\le N}$ with $N \ge \max\{a,b\}+1$.  Since each
$T^{(\le N)}(u)$ satisfies the finite RTT relation, the chosen
coefficient vanishes in the limit.  Thus $T(u)$ lies in
$\widehat Y_{\mathrm{RTT}}$.

The constructions are inverse to one another: truncating the recovered
formal RTT matrix returns the original compatible family, and taking the
stable coefficients of a formal RTT matrix recovers it exactly.  Hence
$q$ is an isomorphism.
\end{proof}

\begin{corollary}[Standard RTT tower satisfies the M-level MC4 package;
\ClaimStatusProvedHere]
\label{cor:yangian-standard-mc4-package}
For the standard RTT truncation tower, the completed bar object
\[
\widehat{\bar B}(Y) := \varprojlim_N \bar B(Y_{\le N})
\]
has continuous bar and cobar differentials, and the canonical
comparison map
\[
\Omega\bigl(\widehat{\bar B}(Y)\bigr) \xrightarrow{\sim}
\widehat Y_{\mathrm{RTT}}
\]
is a quasi-isomorphism.
Thus the standard RTT tower supplies the full M-level completed
bar-cobar package for the coefficientwise RTT completion.  What remains
open is the H-level comparison of $\widehat Y_{\mathrm{RTT}}$ with the
dg-shifted Yangian or factorization-theoretic completion.
\end{corollary}

\begin{proof}
The finite RTT stages lie in the proved $\Eone$-Koszul regime, so the
finite-stage bar-cobar quasi-isomorphisms are already available.
Proposition~\ref{prop:inverse-limit-differential-continuity} supplies
continuity of the completed bar and cobar differentials, and
Corollary~\ref{cor:yangian-weight-cutoff} supplies the
Mittag--Leffler/stabilization input for the standard RTT tower.
Applying Proposition~\ref{prop:mc4-reduction-principle} to that tower
and identifying the target inverse limit by
Proposition~\ref{prop:yangian-rtt-completion-identification} gives the
stated quasi-isomorphism.
\end{proof}

\begin{corollary}[H-level comparison criterion for dg-shifted Yangians;
\ClaimStatusProvedHere]
\label{cor:yangian-hlevel-comparison-criterion}
Let $\Ydg_{\cA}$ be a separated complete dg algebra equipped with a
descending RTT-level filtration by closed dg ideals.  Assume:
\begin{enumerate}
\item $\Ydg_{\cA}$ is the inverse limit of its finite RTT-level
  quotients;
\item for each $N$ there is a dg algebra quasi-isomorphism
  \[
  \Ydg_{\cA}/F^{N+1}\Ydg_{\cA} \xrightarrow{\sim} Y_{\le N}
  \]
  compatible with the truncation tower; and
\item the quotient tower inherits bar-cobar comparison maps compatible
  with the standard RTT tower and has continuous completed bar and cobar
  differentials.
\end{enumerate}
Then the induced comparison map
\[
\Ydg_{\cA} \xrightarrow{\sim} \widehat Y_{\mathrm{RTT}}
\]
is a quasi-isomorphism, and $\Ydg_{\cA}$ defines the same completed
M-level bar-cobar object as the standard RTT completion.  Thus the
remaining Yangian H-level frontier is to identify the canonical
formal-moduli target of
Proposition~\ref{prop:yangian-canonical-hlevel-target}, or any chosen
equivalent dg model, with a filtered dg-shifted or factorization model
with theorematic finite RTT quotients.  This is the Yangian half of
Conjecture~\ref{conj:master-infinite-generator}: once such an
RTT-adapted realization is supplied, the remaining coefficient
comparison is the exact packet
\[
\mathsf{K}^{\mathrm{line}}_{a,b}(N)
=\mathsf{K}^{\mathrm{RTT}}_{a,b}(N)
\qquad (0\le a,b\le N),
\]
detected on the boundary strip
$\{\Delta_{a,0}(N)\}_{0\le a\le N}$, not another local RTT
calculation.
\end{corollary}

\begin{proof}
Apply Proposition~\ref{prop:completed-target-comparison} with
$\cA_{\le N}=Y_{\le N}$.  Since the finite RTT truncation maps are
surjective and the quotients of $\Ydg_{\cA}$ are quasi-isomorphic to
them, the Mittag--Leffler input required there is automatic on
cohomology.  The bar-cobar statement then follows from the final part
of Proposition~\ref{prop:completed-target-comparison}, together with
Corollary~\ref{cor:yangian-standard-mc4-package}.
\end{proof}

\begin{proposition}[Standard type-\texorpdfstring{$A$}{A} realization criterion from shared
bar seed and finite RTT quotients; \ClaimStatusProvedHere]
\label{prop:yangian-typea-realization-criterion}
Let $\Ydg_{\cA}$ be a separated complete dg algebra equipped with:
\begin{enumerate}[label=\textup{(\roman*)}]
\item a translation operator;
\item a Maurer--Cartan element $r(z)$;
\item a twisted coproduct; and
\item a descending RTT-level filtration by closed dg ideals
  \[
  F^1\Ydg_{\cA} \supset F^2\Ydg_{\cA} \supset \cdots
  \]
  preserved by all three structures above.
\end{enumerate}
Assume moreover that:
\begin{enumerate}[label=\textup{(\roman*)},resume]
\item $\Ydg_{\cA}\cong \varprojlim_N \Ydg_{\cA}/F^{N+1}\Ydg_{\cA}$;
\item for every $N$ there is a dg algebra quasi-isomorphism
  \[
  \Ydg_{\cA}/F^{N+1}\Ydg_{\cA}\xrightarrow{\sim}Y_{\le N}
  \]
  compatible with the RTT truncation tower, standard evaluation
  modules, and the induced degree-$2$ twisting morphism;
\item the quotient tower inherits bar-cobar comparison maps compatible
  with the standard RTT tower and has continuous completed bar and
  cobar differentials; and
\item on the ordered fundamental evaluation line, the degree-$2$
  coefficient is induced by the same ordered bar twisting morphism as
  on the factorization target, in the sense of
  Proposition~\ref{prop:dg-shifted-factorization-shared-seed}.
\end{enumerate}
Then:
\begin{enumerate}[label=\textup{(\alph*)}]
\item the filtration on $\Ydg_{\cA}$ is RTT-adapted in the sense of
  Definition~\ref{def:rtt-adapted-filtration};
\item the induced comparison map
  \[
  \Ydg_{\cA}\xrightarrow{\sim}\widehat Y_{\mathrm{RTT}}
  \]
  is a quasi-isomorphism, so $\Ydg_{\cA}$ realizes the H-level
  dg-shifted Yangian target for the standard type-$A$ tower; and
\item the local standard type-$A$ DK-4 packet is already closed, so the
  only remaining Yangian input is the already-isolated spectral
  realization of the standard spectral vector seed-and-shift datum.
\end{enumerate}
\end{proposition}

\begin{proof}
Assumptions~\textup{(v)}--\textup{(vii)} are exactly the hypotheses of
Corollary~\ref{cor:yangian-hlevel-comparison-criterion}.  Therefore the
comparison map
\[
\Ydg_{\cA}\xrightarrow{\sim}\widehat Y_{\mathrm{RTT}}
\]
is a quasi-isomorphism, proving~\textup{(b)}.  Since
assumptions~\textup{(i)}--\textup{(vii)} are precisely the data
required in Definition~\ref{def:rtt-adapted-filtration}, this also
proves~\textup{(a)}.

Assumption~\textup{(viii)} is the shared-seed hypothesis of
Proposition~\ref{prop:dg-shifted-factorization-shared-seed}, so the
ordered fundamental degree-$2$ coefficient on the dg-shifted target is
the standard trace-zero Casimir insertion.  Corollary~\ref{cor:yangian-typea-dg-local-closure}
then closes the local dg-shifted packet on the standard type-$A$
tower.  Thus only the DK-5 categorical packet on the completed
fundamental evaluation modules remains.  By
Proposition~\ref{prop:yangian-dg-fundamental-packet-realization},
Proposition~\ref{prop:yangian-dk5-dg-realization-formal}, and
Corollary~\ref{cor:yangian-dk5-dg-packet-ind}, the dg side is already
formal from the canonical completed dg packet and its ind-completion.
Thus the only remaining categorical input is the already-isolated
realization of the standard spectral vector seed-and-shift datum.
This proves~\textup{(c)}.
\end{proof}

\begin{theorem}[Standard type-\texorpdfstring{$A$}{A} Yangian DK-4/DK-5 closure:
seven variant hypotheses; \ClaimStatusProvedHere]
\label{thm:yangian-dk45-closure-variants}%
\label{cor:yangian-typea-realization-plus-compacts}%
\label{cor:yangian-typea-realization-plus-fundamental-packet}%
\label{cor:yangian-typea-realization-plus-core-realization}%
\label{cor:yangian-formal-moduli-plus-core-realization}%
\label{cor:yangian-typea-realization-plus-dg-packet}%
\label{cor:yangian-canonical-realization-plus-one-seed}%
\label{cor:yangian-canonical-realization-plus-vector-line}%
Under any one of the following seven sets of hypotheses, the standard
type-$A$ Yangian DK-4/DK-5 packet closes.
\begin{enumerate}[label=\textup{(\roman*)}]
\item\emph{Realization $+$ compact core.}
  Assume the hypotheses of
  Proposition~\ref{prop:yangian-typea-realization-criterion}.  Assume
  further that the compact cores of
  \(\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})\) and
  \(\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}\)
  are presentable, stable, compactly generated, and exactly equivalent
  in a way compatible with DK-3 on the completed fundamental packet.

\item\emph{Realization $+$ completed fundamental packet.}
  Assume the hypotheses of
  Proposition~\ref{prop:yangian-typea-realization-criterion}.  Assume
  further that the completed dg-shifted and spectral categories are
  presentable, stable, and compactly generated; that their compact
  objects are the smallest full stable idempotent-complete braided
  monoidal subcategories containing the completed fundamental
  evaluation packets; and that there exist exact braided monoidal
  functors between those compact cores whose restrictions to the
  completed fundamental evaluation packets recover the DK-3 transport
  and whose composites are the identity on that packet.

\item\emph{Realization $+$ core realization.}
  Assume the hypotheses of
  Proposition~\ref{prop:yangian-typea-realization-criterion}.  Assume
  further that the completed dg-shifted and spectral categories are
  presentable, stable, and compactly generated, with compact objects
  exactly $\mathcal{C}_Y^\omega$ and $\mathcal{C}_q^\omega$; and that
  those compact cores are exact braided monoidal realizations of the
  proved finite-dimensional factorization DK pair of
  Theorem~\ref{thm:dk-fd-typeA} in the sense of
  Proposition~\ref{prop:yangian-dk5-core-realization}.

\item\emph{Canonical formal-moduli target $+$ core realization.}
  Let $\cA=\mathcal{Y}(\mathfrak{sl}_M)$,
  $\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA}$ be the canonical
  H-level dg target of
  Proposition~\ref{prop:yangian-canonical-hlevel-target}, and let
  $U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ be the canonical associative
  dg model of Proposition~\ref{prop:yangian-canonical-envelope}.
  Assume that the hypotheses of
  Proposition~\ref{prop:yangian-typea-realization-criterion} hold for
  $U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$.  Assume further that the
  completed dg-shifted and spectral categories are presentable, stable,
  and compactly generated, with compact objects exactly
  $\mathcal{C}_{\mathfrak g}^\omega$ and $\mathcal{C}_q^\omega$; and
  that those compact cores are exact braided monoidal realizations of
  the proved finite-dimensional factorization DK pair of
  Theorem~\ref{thm:dk-fd-typeA} in the sense of
  Proposition~\ref{prop:yangian-dk5-core-realization}.

\item\emph{Realization $+$ spectral vector-line realization.}
  Assume the hypotheses of
  Proposition~\ref{prop:yangian-typea-realization-criterion}.  Assume
  further that the spectral compact core admits an exact braided
  monoidal functor $J_q^\omega$ whose restriction to the vector
  evaluation line is an equivalence onto the completed vector spectral
  line, as in
  Proposition~\ref{prop:yangian-dk5-spectral-vector-line}.

\item\emph{Canonical target $+$ one canonical spectral seed
  (equivariant multiplicative locus).}
  As in~\textup{(iv)}, let $\cA=\mathcal{Y}(\mathfrak{sl}_M)$ with
  canonical target
  $U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ satisfying the hypotheses of
  Proposition~\ref{prop:yangian-typea-realization-criterion}.  Assume
  moreover the equivariant multiplicative spectral realization
  hypotheses of
  Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed},
  so that the shift family is intrinsic and the single canonical
  spectral seed $V^\omega(0):=J_q^\omega(V(0))$ is defined.

\item\emph{Canonical target $+$ spectral vector-line realization.}
  As in~\textup{(iv)}, let $\cA=\mathcal{Y}(\mathfrak{sl}_M)$ with
  canonical target
  $U^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ satisfying the hypotheses of
  Proposition~\ref{prop:yangian-typea-realization-criterion}.  Assume
  further that the spectral compact core admits an exact braided
  monoidal functor
  \(J_q^\omega\colon
  \operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
  \longrightarrow \mathcal C_q^\omega\)
  whose restriction to the vector evaluation line is an equivalence
  onto the completed vector spectral line, as in
  Proposition~\ref{prop:yangian-dk5-spectral-vector-line}.
\end{enumerate}
\end{theorem}

\begin{proof}
In each variant, Proposition~\ref{prop:yangian-typea-realization-criterion}
(applied directly or via its canonical specialization) closes the local
DK-4 packet on the standard type-$A$ tower.

\textup{(i)}
The compact-core equivalence is the input of
Corollary~\ref{cor:yangian-dk5-compact-core}, which closes DK-5.

\textup{(ii)}
The three additional hypotheses are the input of
Corollary~\ref{cor:yangian-dk5-fundamental-packet}, which closes DK-5.

\textup{(iii)}
The compact-core realization is the input of
Corollary~\ref{cor:yangian-dk5-core-realization}, which closes DK-5.

\textup{(iv)}
Proposition~\ref{prop:yangian-canonical-envelope} identifies the dg
model with the canonical formal-moduli target.  The compact-core
hypotheses reduce to variant~\textup{(iii)} with
$\mathcal{C}_Y^\omega$ realized inside
$\operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})$ as
$\mathcal{C}_{\mathfrak g}^\omega$.

\textup{(v)}
Propositions~\ref{prop:yangian-dk5-dg-extension-existence},
\ref{prop:yangian-dk5-dg-realization-formal}, and
Corollary~\ref{cor:yangian-dk5-dg-packet-ind} close the dg side.
On the spectral side, the vector-line hypothesis, together with
the seed-and-shift construction
(Propositions~\ref{prop:yangian-dk5-spectral-seed-shift-construction}
and~\ref{prop:yangian-dk5-spectral-core-shifts},
Corollary~\ref{cor:yangian-dk5-spectral-seed-realization}), satisfies
the input of Corollary~\ref{cor:yangian-dk5-core-realization}, so
DK-5 closes.

\textup{(vi)}
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed}
makes the hypotheses of
Corollary~\ref{cor:yangian-dk5-spectral-one-seed} automatic.  The
completed vector line, fundamental packet, spectral compact core, and
ambient spectral category are all formal, so
variant~\textup{(vii)} is satisfied.

\textup{(vii)}
The vector-line hypothesis is the remaining spectral input of
variant~\textup{(v)} specialized to the canonical target.
\end{proof}

%% ---------------------------------------------------------------
%% The seven individual corollaries below are consolidated into
%% Theorem~\ref{thm:yangian-dk45-closure-variants} above.
%% They are retained for reference and for the detailed proofs.
%% ---------------------------------------------------------------
\iffalse
\begin{corollary}[Standard type-\texorpdfstring{$A$}{A} DK-4/DK-5 closure from realization
and compact core; \ClaimStatusProvedHere]
\label{cor:yangian-typea-realization-plus-compacts}
Assume the hypotheses of
Proposition~\ref{prop:yangian-typea-realization-criterion}.  Assume
further that the compact cores of
\[
\operatorname{Mod}^{\mathrm{comp}}(\Ydg_{\cA})
\qquad\text{and}\qquad
\operatorname{Rep}^{\mathrm{spec}}(\QGspec(R_{\cA}))^{\mathrm{op}}
\]
are presentable, stable, compactly generated, and exactly equivalent in
a way compatible with DK-3 on the completed fundamental packet.  Then
the standard type-$A$ Yangian DK-4/DK-5 packet closes.

Equivalently, once the H-level dg-shifted realization is constructed on
the shared-bar-seed finite-quotient locus, the only remaining step is
the compact-core equivalence, and that step closes DK-5 formally.
\end{corollary}

\begin{proof}
By Proposition~\ref{prop:yangian-typea-realization-criterion}, the
H-level dg-shifted realization exists and the local standard type-$A$
DK-4 packet is already closed.  The additional compact-core hypothesis
is exactly the input of
Corollary~\ref{cor:yangian-dk5-compact-core}, which therefore closes
DK-5.  This proves the full DK-4/DK-5 claim.
\end{proof}

\begin{corollary}[Standard type-\texorpdfstring{$A$}{A} DK-4/DK-5 closure from realization
and completed fundamental packet; \ClaimStatusProvedHere]
\label{cor:yangian-typea-realization-plus-fundamental-packet}
Assume the hypotheses of
Proposition~\ref{prop:yangian-typea-realization-criterion}.  Assume
further that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the completed dg-shifted and spectral categories are presentable,
  stable, and compactly generated;
\item their compact objects are the smallest full stable
  idempotent-complete braided monoidal subcategories containing the
  completed fundamental evaluation packets; and
\item there exist exact braided monoidal functors between those compact
  cores whose restrictions to the completed fundamental evaluation
  packets recover the DK-3 transport and whose composites are the
  identity on that packet.
\end{enumerate}
Then the standard type-$A$ Yangian DK-4/DK-5 packet closes.

Equivalently, once the shared-bar-seed finite-quotient realization
package is in place, the only remaining categorical step is transport
on the completed fundamental evaluation packet; the compact-core
equivalence and the completed comparison functor are then formal.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:yangian-typea-realization-criterion} supplies the
H-level dg-shifted realization and closes the local standard type-$A$
DK-4 packet.  The additional hypotheses are exactly the input of
Corollary~\ref{cor:yangian-dk5-fundamental-packet}, which closes DK-5.
\end{proof}

\begin{corollary}[Standard type-\texorpdfstring{$A$}{A} DK-4/DK-5 closure from dg-shifted
realization and compact-core realization of the proved
finite-dimensional factorization DK core; \ClaimStatusProvedHere]
\label{cor:yangian-typea-realization-plus-core-realization}
Assume the hypotheses of
Proposition~\ref{prop:yangian-typea-realization-criterion}.  Assume
further that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the completed dg-shifted and spectral categories are presentable,
  stable, and compactly generated, with compact objects exactly
  $\mathcal{C}_Y^\omega$ and $\mathcal{C}_q^\omega$; and
\item those compact cores are exact braided monoidal realizations of
  the proved finite-dimensional factorization DK pair of
  Theorem~\ref{thm:dk-fd-typeA} in the sense of
  Proposition~\ref{prop:yangian-dk5-core-realization}.
\end{enumerate}
Then the standard type-$A$ Yangian DK-4/DK-5 packet closes.

Equivalently, once the shared-bar-seed finite-quotient realization
package is in place, the remaining categorical step is to realize the
compact cores as exact braided monoidal completions of the already
proved finite-dimensional factorization DK core.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:yangian-typea-realization-criterion} supplies the
H-level dg-shifted realization and closes the local standard type-$A$
DK-4 packet.  The additional hypotheses are exactly the input of
Corollary~\ref{cor:yangian-dk5-core-realization}, which closes DK-5.
\end{proof}

\begin{corollary}[Canonical formal-moduli Yangian target closes
DK-4/DK-5 once the compact cores realize the proved finite-dimensional
DK core; \ClaimStatusProvedHere]
\label{cor:yangian-formal-moduli-plus-core-realization}
Let
\[
\cA=\mathcal{Y}(\mathfrak{sl}_M),
\qquad
\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA}
\]
be the canonical H-level dg target of
Proposition~\ref{prop:yangian-canonical-hlevel-target}, and let
\[
U^{\mathrm{comp}}(\mathfrak{g}_{\cA})
\]
be the canonical associative dg model of
Proposition~\ref{prop:yangian-canonical-envelope}.  Assume that the
hypotheses of Proposition~\ref{prop:yangian-typea-realization-criterion}
hold for \(U^{\mathrm{comp}}(\mathfrak{g}_{\cA})\).  Assume further
that:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the completed dg-shifted and spectral categories are presentable,
  stable, and compactly generated, with compact objects exactly
  $\mathcal{C}_{\mathfrak g}^\omega$ and $\mathcal{C}_q^\omega$; and
\item those compact cores are exact braided monoidal realizations of
  the proved finite-dimensional factorization DK pair of
  Theorem~\ref{thm:dk-fd-typeA} in the sense of
  Proposition~\ref{prop:yangian-dk5-core-realization}.
\end{enumerate}
Then the standard type-$A$ Yangian DK-4/DK-5 packet closes.

Equivalently, the canonical formal-moduli target already exists.  Once
its canonical completed enveloping dg algebra carries the RTT-adapted
finite-quotient/shared-seed package and its compact core is realized as
an exact braided monoidal completion of the proved finite-dimensional
factorization DK core, the compact-core DK-5 equivalence and the
completed comparison are formal.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:yangian-typea-realization-criterion} applies to
\(U^{\mathrm{comp}}(\mathfrak{g}_{\cA})\), so this dg algebra model realizes the
standard type-$A$ H-level Yangian target and closes the local DK-4
packet on the canonical formal-moduli target by
Proposition~\ref{prop:yangian-canonical-envelope}.  The additional
hypotheses are exactly the compact-core realization input of
Corollary~\ref{cor:yangian-typea-realization-plus-core-realization},
with \(\mathcal{C}_Y^\omega\) realized inside
\(\operatorname{Mod}^{\mathrm{comp}}(\mathfrak{g}_{\cA})\) as
\(\mathcal{C}_{\mathfrak g}^\omega\).  Therefore DK-5 closes.
\end{proof}

\begin{corollary}[Standard type-\texorpdfstring{$A$}{A} DK-4/DK-5 closure from spectral
vector-line realization; \ClaimStatusProvedHere]
\label{cor:yangian-typea-realization-plus-dg-packet}
Assume the hypotheses of
Proposition~\ref{prop:yangian-typea-realization-criterion}.  Assume
further that the spectral compact core admits an exact braided monoidal
functor \(J_q^\omega\) whose restriction to the vector evaluation line
is an equivalence onto the completed vector spectral line, as in
Proposition~\ref{prop:yangian-dk5-spectral-vector-line}.
Then the standard type-$A$ Yangian DK-4/DK-5 packet closes.

Equivalently, once the shared-bar-seed finite-quotient realization
package is in place, the dg half of DK-5 is already closed by the
canonical dg compact-core realization and its ind-completion, and the
ambient spectral category is formal from ind-completion of the spectral
compact core.

The only remaining categorical input is therefore the
realization of the standard spectral vector seed-and-shift datum; on
the multiplicative spectral realization locus,
Corollary~\ref{cor:yangian-dk5-spectral-factorization-vector-line}
shows that vector-line realization already suffices, and
Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line}
shows that the compact core itself is then forced as the thick
braided-monoidal closure of that line inside the ambient ordered
factorization category, and
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-vector-line}
packages the resulting spectral DK-5 closure directly from that ambient
vector-line realization.

While
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}
and
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-one-seed}
and
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-schur-seed}
sharpen this further to one Schur-simple ambient vector seed together
with the one-parameter trigonometric seed-pair identity on its
dilation orbit, and
Corollary~\ref{cor:yangian-dk5-spectral-factorization-seed-single-line}
shows that under diagonal \(\mathfrak{sl}_M\)-equivariance and
highest-weight normalization this local packet contracts to one ordered
mixed-tensor line, while on the
equivariant multiplicative spectral realization locus of
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed},
the seed and shift data are intrinsic.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:yangian-typea-realization-criterion} supplies the
H-level dg-shifted realization and closes the local standard type-$A$
DK-4 packet.  Proposition~\ref{prop:yangian-dk5-dg-extension-existence}
constructs the exact braided monoidal dg packet extension
\(J_Y^\omega\), Proposition~\ref{prop:yangian-dk5-dg-realization-formal}
makes it an equivalence onto the dg compact core, and
Corollary~\ref{cor:yangian-dk5-dg-packet-ind} constructs the ambient dg
module category as the ind-completion of that core.  Thus the dg side
already satisfies the dg half of the input of
Corollary~\ref{cor:yangian-dk5-core-realization}.  By
Proposition~\ref{prop:quantum-fd-vector-seed-shifts},
Propositions~\ref{prop:yangian-dk5-spectral-seed-shift-construction}
and~\ref{prop:yangian-dk5-spectral-core-shifts}, together with
Corollary~\ref{cor:yangian-dk5-spectral-seed-realization}, the same is
true on the spectral side with compact core \(\mathcal{C}_q^\omega\);
on the multiplicative spectral realization locus,
Corollary~\ref{cor:yangian-dk5-spectral-factorization-vector-line}
shows that vector-line realization already supplies the whole spectral
packet, and
Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line}
constructs the compact core itself as the thick braided-monoidal
closure of that line in the ambient ordered factorization category;
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-vector-line}
then packages the whole spectral DK-5 side directly from that ambient
vector-line realization;
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}
and
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-one-seed}
and
Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-schur-seed}
show that, more sharply, one Schur-simple ambient vector seed already
supplies the whole object-level ambient route, while
Corollary~\ref{cor:yangian-dk5-spectral-factorization-seed-trig}
identifies the remaining explicit local comparison there with the
one-parameter trigonometric seed-pair identity on its dilation orbit,
and Corollary~\ref{cor:yangian-dk5-spectral-factorization-seed-single-line}
shows that under diagonal \(\mathfrak{sl}_M\)-equivariance and
highest-weight normalization this contracts further to one ordered
mixed-tensor line, and
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-exchange}
sharpens that line to one scalar exchange coefficient family;
Corollary~\ref{cor:yangian-dk5-spectral-factorization-seed-exchange-mult}
shows that this scalar family already descends to the multiplicative
spectral ratio; equivalently,
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-alt-mult}
rewrites it as one antisymmetric-channel character there;
and on the sharper equivariant multiplicative spectral
realization locus,
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed}
removes the seed and shift data as independent choices.
Hence the hypotheses of
Corollary~\ref{cor:yangian-dk5-core-realization} are satisfied, so
DK-5 closes.
\end{proof}
\fi
%% --- end of first \iffalse block (closures i--v) ---

\begin{corollary}[Canonical formal-moduli Yangian target: exact
remaining input after RTT-adapted realization;
\ClaimStatusProvedHere]
\label{cor:yangian-canonical-realization-to-spectral-seed}
Let
\[
\cA=\mathcal{Y}(\mathfrak{sl}_M),
\qquad
\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA}
\]
be the canonical H-level dg target of
Proposition~\ref{prop:yangian-canonical-hlevel-target}, and let
\[
U^{\mathrm{comp}}(\mathfrak{g}_{\cA})
\]
be its canonical associative dg model of
Proposition~\ref{prop:yangian-canonical-envelope}.  Assume that the
hypotheses of Proposition~\ref{prop:yangian-typea-realization-criterion}
hold for \(U^{\mathrm{comp}}(\mathfrak{g}_{\cA})\).  Then the canonical
formal-moduli target already carries the standard type-$A$ H-level dg
realization, the local DK-4 packet is closed, and the dg compact-core
side of DK-5 is formal.

Assume moreover that the spectral compact core \(\mathcal C_q^\omega\)
is realized as a full stable idempotent-complete braided-monoidal
subcategory of
\[
\Factord(\bC^\times;\QGspec(R_{\cA}))
\]
closed under the multiplicative dilations
\(\rho_a(z)=e^a z\), and that the exact braided-monoidal functor
\[
J_q^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\longrightarrow
\mathcal C_q^\omega
\]
intertwines the source loop-rotation family
\(\mathsf T_a^{\mathrm{fd}}\) with the target pullback family
\(\rho_a^*\).  Define
\[
V^\omega(0):=J_q^\omega(V(0)).
\]
Then the hypotheses of
Corollary~\ref{cor:yangian-dk5-spectral-one-seed} are automatic.
Equivalently, on the canonical Yangian target, equivariant
multiplicative spectral realization removes the shift datum and the
base vector seed as independent inputs: the shift family is intrinsic
and the seed is canonical.

Equivalently, on the canonical Yangian target the only remaining
standard type-$A$ input is realization of the standard spectral vector
seed-and-shift datum in the spectral compact core; on the equivariant
multiplicative spectral realization locus, this contracts further to
the realization functor together with one ambient compatible
Schur-simple vector seed whose dilation orbit gives the spectral
vector line together with the one-parameter trigonometric seed-pair
identity on that orbit, and under diagonal
\(\mathfrak{sl}_M\)-equivariance and highest-weight normalization even
that local packet contracts first to one ordered mixed-tensor line and
then to one scalar exchange coefficient family.

Once
that ambient seed is placed
Corollary~\ref{cor:yangian-dk5-spectral-factorization-vector-line}
and Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line}
and Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-vector-line}
and Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-line}
and Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-one-seed}
and Corollary~\ref{cor:yangian-dk5-spectral-factorization-ambient-schur-seed}
and Corollary~\ref{cor:yangian-dk5-spectral-factorization-seed-trig}
and Corollary~\ref{cor:yangian-dk5-spectral-factorization-seed-single-line}
and Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-exchange}
and Corollary~\ref{cor:yangian-dk5-spectral-factorization-seed-exchange-mult}
and Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-alt-mult}
make the rest formal.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:yangian-typea-realization-criterion} applied to
\(U^{\mathrm{comp}}(\mathfrak{g}_{\cA})\) gives the standard type-$A$
RTT-adapted dg realization, closes the local DK-4 packet, and reduces
the remaining input to the standard spectral vector seed-and-shift
datum.  Proposition~\ref{prop:yangian-canonical-envelope} identifies
this dg model with the canonical formal-moduli target.

Under the additional multiplicative-spectral hypothesis,
Proposition~\ref{prop:yangian-dk5-spectral-factorization-shifts}
constructs the target shift family intrinsically as pullback along the
dilations \(\rho_a\), while the displayed definition makes the base
vector seed canonical.  The assumed equivariance of \(J_q^\omega\)
with respect to source loop rotation and target pullback is exactly the
remaining compatibility hypothesis of
Corollary~\ref{cor:yangian-dk5-spectral-one-seed}.  Therefore that
corollary applies and removes any separate seed-and-shift choice on the
canonical target.  The final sentence is exactly this reformulation on
the canonical target.
\end{proof}

\begin{corollary}[Canonical formal-moduli Yangian target: the local
spectral packet contracts to one mixed-tensor line on the equivariant
multiplicative locus; \ClaimStatusProvedHere]
\label{cor:yangian-canonical-realization-to-single-line}
Assume the hypotheses of
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed}.
For \(c\in\mathbb C\), define
\[
V^\omega(c):=\rho_c^*V^\omega(0),
\]
and let
\[
\mathsf B_{0,c}^{\omega}\colon
V^\omega(0)\boxtimes V^\omega(c)
\xrightarrow{\sim}
V^\omega(c)\boxtimes V^\omega(0)
\]
be the associated ambient seed-pair braid operator on the realized
spectral compact core.  Assume moreover that for every \(c\in\mathbb C\):
\begin{enumerate}[label=\textup{(\roman*)}]
\item \(\mathsf B_{0,c}^{\omega}\) intertwines the diagonal
  \(\mathfrak{sl}_M\)-action;
\item \(\mathsf B_{0,c}^{\omega}\) agrees with the standard source
  operator on the highest-weight line:
  \[
  \mathsf B_{0,c}^{\omega}(e_1\otimes e_1)
  =
  \mathsf B_{0,c}^{\mathrm{fd}}(e_1\otimes e_1).
  \]
\end{enumerate}
Then the remaining explicit local spectral comparison on the canonical
target is exactly the one-parameter mixed-tensor identity
\[
\mathsf B_{0,c}^{\omega}(e_1\otimes e_2)
=
\mathsf B_{0,c}^{\mathrm{fd}}(e_1\otimes e_2)
\qquad (c\in\mathbb C).
\]

Equivalently, on the equivariant multiplicative spectral realization
locus of the canonical target, once the seed and shift data are
canonical and the diagonal symmetry/highest-weight normalization are in
place, the local spectral packet is no longer a whole trigonometric
family: it contracts to one ordered mixed-tensor line family.
\end{corollary}

\begin{proof}
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed}
constructs the canonical seed \(V^\omega(0)\) and the intrinsic shift
family \(\rho_c^*\) on the equivariant multiplicative spectral
realization locus.  Therefore the ambient seed-pair operators
\(\mathsf B_{0,c}^{\omega}\) are exactly the operators to which
Corollary~\ref{cor:yangian-dk5-spectral-factorization-seed-single-line}
applies, with \(V^{\mathrm{mult}}(0)=V^\omega(0)\).  The two extra
hypotheses here are precisely the diagonal
\(\mathfrak{sl}_M\)-equivariance and highest-weight normalization
hypotheses required there.  Hence that corollary identifies the
remaining local spectral comparison with the displayed mixed-tensor
family.
\end{proof}

\begin{corollary}[Canonical formal-moduli Yangian target: the local
spectral packet contracts to one exchange coefficient family on the
equivariant multiplicative locus; \ClaimStatusProvedHere]
\label{cor:yangian-canonical-realization-to-exchange}
Assume the hypotheses of
Corollary~\ref{cor:yangian-canonical-realization-to-single-line}, and
assume \(M\ge 2\).  For every \(c\in\mathbb C\), write uniquely
\[
\mathsf B_{0,c}^{\omega}(e_1\otimes e_2)
=
\alpha^\omega(c)\,e_1\otimes e_2
+\beta^\omega(c)\,e_2\otimes e_1
\]
and
\[
\mathsf B_{0,c}^{\mathrm{fd}}(e_1\otimes e_2)
=
\alpha^{\mathrm{fd}}(c)\,e_1\otimes e_2
+\beta^{\mathrm{fd}}(c)\,e_2\otimes e_1.
\]
Then the remaining explicit local spectral comparison on the canonical
target is exactly the scalar identity
\[
\beta^\omega(c)=\beta^{\mathrm{fd}}(c)
\qquad (c\in\mathbb C).
\]

Equivalently, on the equivariant multiplicative spectral realization
locus of the canonical target, once the seed and shift data are
canonical and the diagonal symmetry/highest-weight normalization are in
place, the local spectral packet contracts from one ordered
mixed-tensor line family to one scalar exchange coefficient family.
\end{corollary}

\begin{proof}
Corollary~\ref{cor:yangian-canonical-realization-to-single-line}
identifies the remaining local spectral comparison on the canonical
target with the mixed-tensor family
\[
\mathsf B_{0,c}^{\omega}(e_1\otimes e_2)
=
\mathsf B_{0,c}^{\mathrm{fd}}(e_1\otimes e_2)
\qquad (c\in\mathbb C).
\]
Now apply
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-exchange}
with \(V^{\mathrm{mult}}(0)=V^\omega(0)\) and
\(\mathsf B_{0,c}^{\mathrm{mult}}=\mathsf B_{0,c}^{\omega}\).
\end{proof}

\begin{corollary}[Canonical formal-moduli Yangian target: the local
spectral packet descends to one multiplicative-ratio scalar family;
\ClaimStatusProvedHere]
\label{cor:yangian-canonical-realization-to-exchange-mult}
Assume the hypotheses of
Corollary~\ref{cor:yangian-canonical-realization-to-exchange}.  Then
\[
\beta^\omega(c+2\pi i)=\beta^\omega(c)
\qquad (c\in\mathbb C),
\]
so the canonical-target exchange coefficient descends uniquely to a
scalar function
\[
\beta_\times^\omega
\]
of the multiplicative spectral ratio with
\[
\beta^\omega(c)=\beta_\times^\omega(e^c).
\]
The remaining explicit local spectral comparison on the canonical
target is therefore exactly
\[
\beta_\times^\omega=\beta_\times^{\mathrm{fd}}.
\]

Equivalently, on the equivariant multiplicative spectral realization
locus of the canonical target, the local spectral packet is one scalar
function on the multiplicative spectral line, not a family on its
additive logarithmic cover.
\end{corollary}

\begin{proof}
By
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed},
the canonical target shift family is the ambient dilation pullback
family \(\rho_c^*\), so
\[
V^\omega(c)=\rho_c^*V^\omega(0).
\]
Since \(\rho_{c+2\pi i}=\rho_c\), one has
\[
V^\omega(c+2\pi i)=V^\omega(c)
\]
and therefore
\[
\mathsf B_{0,c+2\pi i}^{\omega}
=
\mathsf B_{0,c}^{\omega}.
\]
Taking the coefficient of \(e_2\otimes e_1\) in the expansion of
\(\mathsf B_{0,c}^{\omega}(e_1\otimes e_2)\) gives the displayed
periodicity of \(\beta^\omega(c)\).  The source side already descends
by
Corollary~\ref{cor:yangian-dk5-spectral-factorization-seed-exchange-mult},
so the final identity is just
Corollary~\ref{cor:yangian-canonical-realization-to-exchange}
rewritten on the multiplicative ratio line.
\end{proof}

\begin{corollary}[Canonical formal-moduli Yangian target: the local
spectral packet is the antisymmetric-channel character on the
multiplicative spectral line; \ClaimStatusProvedHere]
\label{cor:yangian-canonical-realization-to-alt-mult}
Assume the hypotheses of
Corollary~\ref{cor:yangian-canonical-realization-to-exchange-mult}, and
assume \(M\ge 2\).  Then there exists a unique scalar function
\[
\lambda_{\mathrm{alt},\times}^{\omega}
\]
of the multiplicative spectral ratio such that
\[
\mathsf B_{0,c}^{\omega}
(e_1\otimes e_2-e_2\otimes e_1)
=
\lambda_{\mathrm{alt},\times}^{\omega}(e^c)
(e_1\otimes e_2-e_2\otimes e_1).
\]
The remaining explicit local spectral comparison on the canonical
target is exactly
\[
\lambda_{\mathrm{alt},\times}^{\omega}
=
\lambda_{\mathrm{alt},\times}^{\mathrm{fd}}.
\]

Equivalently, on the equivariant multiplicative spectral realization
locus of the canonical target, the local spectral packet is one scalar
character on the highest-weight antisymmetric channel over the
multiplicative spectral line.
\end{corollary}

\begin{proof}
Apply
Proposition~\ref{prop:yangian-dk5-spectral-factorization-seed-alt-mult}
with \(V^{\mathrm{mult}}(0)=V^\omega(0)\) and
\(\mathsf B_{0,c}^{\mathrm{mult}}=\mathsf B_{0,c}^{\omega}\).  The
hypotheses needed there are exactly those supplied by
Corollary~\ref{cor:yangian-canonical-realization-to-exchange-mult}.
\end{proof}

%% --- second \iffalse block (closures vi--vii) ---
\iffalse
\begin{corollary}[Canonical formal-moduli Yangian target closes
DK-4/DK-5 from one canonical spectral seed on the equivariant
multiplicative locus; \ClaimStatusProvedHere]
\label{cor:yangian-canonical-realization-plus-one-seed}
Assume the hypotheses of
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed}.
Then the standard type-$A$ Yangian DK-4/DK-5 packet closes on the
canonical formal-moduli target.

Equivalently, once the canonical completed enveloping dg algebra
\(U^{\mathrm{comp}}(\mathfrak{g}_{\cA})\) carries the RTT-adapted
finite-quotient/shared-seed package and the spectral compact core is
realized equivariantly for multiplicative dilations, it is enough to
place the single canonical spectral seed
\[
V^\omega(0):=J_q^\omega(V(0)).
\]
The shift family is then intrinsic, the full spectral vector packet is
forced, and DK-4/DK-5 closes on the canonical target.
\end{corollary}

\begin{proof}
Corollary~\ref{cor:yangian-canonical-realization-to-spectral-seed}
makes the hypotheses of
Corollary~\ref{cor:yangian-dk5-spectral-one-seed} automatic on the
canonical target.  Therefore the completed vector line, ordered vector
packet, completed fundamental packet, ordered tensor-generator packet,
spectral compact core, and ambient spectral category are all formal.
In particular, the vector-line hypothesis of
Corollary~\ref{cor:yangian-canonical-realization-plus-vector-line} is
satisfied.  Applying that corollary closes DK-4/DK-5.
\end{proof}

\begin{corollary}[Canonical formal-moduli Yangian target closes
DK-4/DK-5 from spectral vector-line realization;
\ClaimStatusProvedHere]
\label{cor:yangian-canonical-realization-plus-vector-line}
Let
\[
\cA=\mathcal{Y}(\mathfrak{sl}_M),
\qquad
\mathfrak{g}_{\cA}:=T_*\mathfrak{F}_{\cA}
\]
be the canonical H-level dg target of
Proposition~\ref{prop:yangian-canonical-hlevel-target}, and let
\[
U^{\mathrm{comp}}(\mathfrak{g}_{\cA})
\]
be its canonical associative dg model of
Proposition~\ref{prop:yangian-canonical-envelope}.  Assume that the
hypotheses of Proposition~\ref{prop:yangian-typea-realization-criterion}
hold for \(U^{\mathrm{comp}}(\mathfrak{g}_{\cA})\).  Assume further
that the spectral compact core admits an exact braided monoidal functor
\[
J_q^\omega\colon
\operatorname{Fact}_{\Eone}^{\mathrm{fd}}(U_q(\mathfrak{sl}_M))^{\mathrm{op}}
\longrightarrow
\mathcal C_q^\omega
\]
whose restriction to the vector evaluation line is an equivalence onto
the completed vector spectral line, as in
Proposition~\ref{prop:yangian-dk5-spectral-vector-line}.  Then the
standard type-$A$ Yangian DK-4/DK-5 packet closes on the canonical
formal-moduli target.

Equivalently, once the canonical completed enveloping dg algebra
carries the RTT-adapted finite-quotient/shared-seed package, it is
enough to realize the standard vector evaluation line on the spectral
side.  The dg compact core and ambient dg category are already formal,
and the spectral compact core, ambient spectral category, compact-core
comparison, and completed comparison then become formal as well.  On
the multiplicative spectral factorization locus,
Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line}
shows that the spectral compact core is forced as the thick
braided-monoidal closure of that realized vector line.
\end{corollary}

\begin{proof}
Proposition~\ref{prop:yangian-typea-realization-criterion} applies to
\(U^{\mathrm{comp}}(\mathfrak{g}_{\cA})\), so the canonical
formal-moduli target already carries the standard type-$A$ dg-shifted
realization and the local DK-4 packet is closed.  The additional
vector-line hypothesis is exactly the remaining spectral input of
Corollary~\ref{cor:yangian-typea-realization-plus-dg-packet}, so that
corollary applies and closes DK-4/DK-5 on the canonical target.  The
final sentence is the multiplicative factorization refinement supplied
by Proposition~\ref{prop:yangian-dk5-spectral-factorization-core-from-vector-line}.
\end{proof}
\fi
%% --- end of second \iffalse block (closures vi--vii) ---

\begin{remark}[Rational vs.\ trigonometric DK]
\label{rem:rational-trigonometric-dk}
\index{Drinfeld--Kohno!rational vs trigonometric}
The DK square takes different forms depending on the $R$-matrix type:

\emph{Rational DK}
\textup{(}Theorem~\textup{\ref{thm:derived-dk-yangian})}.
The Yangian $R$-matrix $R(u) = 1 - \hbar P/u$ is rational
in the additive spectral parameter $u$.  Koszul duality sends
$\hbar \to -\hbar$, i.e., $R(u) \to R^{-1}(u)$.  The bar
complex uses the propagator $d\log(z_i - z_j)$ on the
FM compactification of $\bC$.

\emph{Trigonometric DK}
\textup{(}Remark~\textup{\ref{rem:yangian-quantum-group})}.
The quantum loop algebra $U_q(\widehat{\mathfrak{g}})$ has
trigonometric $R$-matrix $R(u/v)$ in the multiplicative
parameter.  Koszul duality sends $q \to q^{-1}$.  The bar
complex uses the propagator $d\log(z_i/z_j)$ on the
FM compactification of $\bC^\times$.

The Kazhdan functor $\Phi_K$ intertwines the rational and
trigonometric pictures via the exponential map $u \mapsto e^u$,
$\bC \to \bC^\times$.  The DK
square~\eqref{eq:dk-square-yangian} encodes the commutativity
of this intertwining with bar-cobar duality.
\end{remark}

The Yangian chapter reveals the $\Eone$-chiral face of the theory.
The chain-level / evaluation-locus derived Drinfeld--Kohno theorem
(Theorems~\ref{thm:derived-dk-affine}
and~\ref{thm:derived-dk-yangian}) proves that bar-cobar duality
\emph{geometrically implements} the quantum group involution
$q \mapsto q^{-1}$, via orientation reversal on ordered
configuration spaces.  The $\Einf$-chiral examples of the preceding
chapters all have commutative factorization structure; the Yangian is
the first object whose Koszul duality intertwines genuinely
noncommutative (braided) monoidal data.  The theorematic endpoint is
DK-2/3 for finite-dimensional type~$A$
(Theorem~\ref{thm:dk-fd-typeA}), which extends the evaluation-locus
factorization comparison (Theorem~\ref{thm:factorization-dk-eval})
to all finite-dimensional representations via thick generation.
The remaining frontier is
the extension to category~$\mathcal{O}$ and other types,
followed by the staged passage through DK-4/DK-5
(dg-shifted/triple-bridge comparison), which is the natural
$\Eone$-chiral bridge to the modular Koszul programme
(\S\ref{sec:modular-koszul-programme}).
